\section{StreamName Common-Refinement Source Determinacy}
\label{sec:streamname-common-refinement-source-determinacy}

\begin{theorem}[StreamName common-refinement source determinacy]
\label{thm:streamname-common-refinement-source-determinacy}
Let $\mathcal W_L$ and $\mathcal W_R$ be public finite-window
$\StreamNameUp$ packages over certified observation maps $s,t$, and let
$\mathcal R$ be a certified common-refinement package whose
$\mathsf{ProbeBundle}$ window restricts to the selected windows of
$\mathcal W_L$ and $\mathcal W_R$. Then every $\RegSeqRat$ handoff and every
finite-window $\RealUp$ handoff read from $\mathcal R$ has the same
StreamName source tuple, namely the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$ row, the
displayed $\mathsf{ProbeBundle}$ row, the $\mathsf{InBundle}$ membership rows,
the selected $\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, and the displayed
$\hsame/\Cont/\Pkg$ rows carried by the refinement ledger.

This source tuple is independent of whether the handoff is reached through
$\mathcal W_L$ or through $\mathcal W_R$. It contains no completion data, no
quotient row, no host index equality, no $\RegSeqRat$ regularity row, and no
$\RealUp$ seal classifier.
\end{theorem}
\begin{proof}
First read the common refinement at the public StreamName boundary. Apply
\autoref{thm:streamname-finite-window-common-refinement-export}; its
restriction clauses identify the same finite-window classifier over the
common refinement with the two component windows. Then apply
\autoref{thm:streamname-window-common-refinement-readback} to each selected
observation in the refinement. The selected endpoint rows are exactly the
pointwise $\mathsf{RatHistoryClassifier}$ rows and the finite endpoint
readback rows displayed by the common refinement.

Next pass from the public refinement to the tail-window packet. Apply
\autoref{thm:streamname-tail-window-cover-common-refinement}. The packet over
the generated common window restricts to the two selected subbundles and keeps
the same $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$,
$\mathsf{UnaryHistory}$, pointwise classifier, $\hsame$, $\Cont$, and $\Pkg$
ledger rows.

Now read the downstream handoff. Apply
\autoref{thm:streamname-regseqrat-pointwise-handoff} to the selected
pointwise rows and then apply
\autoref{thm:streamname-real-regseq-obligation-separation}. These two
theorems separate the StreamName source rows from the $\RegSeqRat$ regularity
obligations and from the finite-window $\RealUp$ seal obligation.

The same source tuple is therefore obtained along the left route and along the
right route, because both routes are restrictions of the one displayed
common-refinement packet. Completion objects, quotient rows, host index
equalities, $\RegSeqRat$ regularity rows, and $\RealUp$ seal classifiers have
no constructor in that source packet, so they cannot be part of the determined
source surface.
\end{proof}

\begin{theorem}[StreamName directed common-refinement source associativity]
\label{thm:streamname-directed-common-refinement-source-associativity}
Let $\mathcal W_1$, $\mathcal W_2$, $\mathcal W_3$, and $\mathcal W_4$ be
public finite-window $\StreamNameUp$ packages over the same certified
endpoint maps $s,t$. Let $\mathcal R_{(12)3,4}$ and $\mathcal R_{1(23),4}$
be two directed certified common-refinement trees whose visible leaves are the
same four selected windows, with the first tree grouping
$((\mathcal W_1,\mathcal W_2),\mathcal W_3)$ before comparison with
$\mathcal W_4$, and the second tree grouping
$(\mathcal W_1,(\mathcal W_2,\mathcal W_3))$ before comparison with
$\mathcal W_4$.

Assume each internal common-refinement package restricts to the selected
windows named by its children and carries the displayed certified refinement
ledger. Then the two directed trees expose the same StreamName source tuple:
the row
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$ read from the
common visible refinement, the displayed $\mathsf{ProbeBundle}$ row, the
$\mathsf{InBundle}$ membership rows, the selected $\mathsf{UnaryHistory}$
rows, the pointwise $\mathsf{RatHistoryClassifier}$ rows, and the displayed
$\hsame/\Cont/\Pkg$ ledger rows.

Regrouping the directed common-refinement tree introduces no $\RegSeqRat$
regularity row, no $\RealUp$ seal classifier, no quotient row, no completion
datum, no metric-completeness datum, and no host-index equality. Those rows
remain outside the StreamName source tuple consumed by downstream
$\RegSeqRat$ and terminal finite-window $\RealUp$ readback.
\end{theorem}
\begin{proof}
First compare the two triples before the terminal comparison with
$\mathcal W_4$. Apply
\autoref{thm:streamname-common-refinement-source-triple-confluence} to the
triple $(\mathcal W_1,\mathcal W_2,\mathcal W_3)$ as grouped through
$((\mathcal W_1,\mathcal W_2),\mathcal W_3)$, and apply the same theorem to
the triple as grouped through
$(\mathcal W_1,(\mathcal W_2,\mathcal W_3))$. Both applications read the same
finite-window classifier, bundle, membership, selected history, pointwise
classifier, and $\hsame/\Cont/\Pkg$ ledger surface from the displayed triple
refinement.

Next compare the overlap carried by $\mathcal W_1$ and $\mathcal W_2$. Use
\autoref{thm:streamname-common-refinement-source-confluence}. The overlapping
pair has one displayed StreamName source tuple, so the intermediate packet
seen by either triple grouping has the same classifier, bundle, membership,
selected-history, pointwise-classifier, and provenance rows.

Finally compose the displayed ledger rows by transitivity of the
$\hsame/\Cont/\Pkg$ provenance. The terminal comparison with $\mathcal W_4$
therefore receives the same source tuple from either regrouping. Since
\autoref{thm:streamname-common-refinement-source-confluence} and
\autoref{thm:streamname-common-refinement-source-triple-confluence} separate
that source tuple from $\RegSeqRat$ regularity, $\RealUp$ sealing, quotient,
completion, metric-completeness, and host-index rows, the regrouping cannot
introduce any such row.
\end{proof}

\begin{theorem}[StreamName common-refinement source confluence]
\label{thm:streamname-common-refinement-source-confluence}
Let $\mathcal W_L$ and $\mathcal W_R$ be public finite-window
$\StreamNameUp$ packages over the same certified endpoint maps $s,t$, and let
$\mathcal R$ be a certified common-refinement package whose generated window
restricts to both selected windows. Consider the two finite-window routes
$$
\mathcal R\longrightarrow \mathcal W_L\longrightarrow \RegSeqRat
\quad\text{and}\quad
\mathcal R\longrightarrow \mathcal W_R\longrightarrow \RegSeqRat,
$$
followed by the finite-window $\RealUp$ handoff that reads the induced
regular rational sequence rows. The two routes expose the same downstream
source tuple: the row
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$, the displayed
$\mathsf{ProbeBundle}$, the $\mathsf{InBundle}$ membership rows, the selected
$\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, and the displayed
$\hsame/\Cont/\Pkg$ rows carried by the refinement ledger.

Consequently the induced finite-window $\RealUp$ handoffs read the same
$\DyadicRatCore$ endpoint rows. They do not add completion data, quotient
data, metric-completeness data, host-index equality, or a seal classifier to
the source surface determined by the common refinement.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-common-refinement-source-determinacy}. It identifies
the StreamName source tuple seen from the left selected window with the tuple
seen from the right selected window, because both are restrictions of the one
certified common-refinement packet $\mathcal R$.

Next apply
\autoref{thm:streamname-tail-window-cover-common-refinement}. The generated
tail-window packet over $\mathcal R$ has the same displayed
$\mathsf{ProbeBundle}$ row, the same $\mathsf{InBundle}$ membership rows, the
same selected $\mathsf{UnaryHistory}$ rows, and the same pointwise rational
history classifier rows on both routes.

Now apply \autoref{thm:streamname-regseqrat-pointwise-handoff}. The
$\RegSeqRat$ boundary consumes exactly those pointwise rational rows and the
displayed $\hsame/\Cont/\Pkg$ ledger rows; it does not introduce an additional
route-dependent source coordinate.

Finally apply \autoref{thm:streamname-real-regseq-obligation-separation}. The
finite-window $\RealUp$ handoff reads the induced $\DyadicRatCore$ endpoint
rows from the already identified regular rational sequence surface, while the
seal obligation remains separate from the StreamName source tuple. Thus the
left route and the right route compose to the same downstream
$\RegSeqRat/\RealUp$ source surface, with no completion, quotient,
metric-completeness, host-index, or seal-classifier row added to that surface.
\end{proof}

\begin{theorem}[StreamName common-refinement RealUp seal confluence]
\label{thm:streamname-common-refinement-real-seal-confluence}
Let $\mathcal W_L$ and $\mathcal W_R$ be public finite-window
$\StreamNameUp$ packages over the same certified endpoint maps $s,t$, and let
$\mathcal R$ be a certified common-refinement package whose generated window
restricts to both selected windows. Let $\mathcal E_L$ and $\mathcal E_R$ be
finite-window $\RealUp$ seal packages induced from $\mathcal R$ through the
left and right $\RegSeqRat$ routes
$$
\mathcal R\longrightarrow \mathcal W_L\longrightarrow \RegSeqRat
\quad\text{and}\quad
\mathcal R\longrightarrow \mathcal W_R\longrightarrow \RegSeqRat.
$$
Then $\mathcal E_L$ and $\mathcal E_R$ expose the same visible seal source.
That source is the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$ row, the
displayed $\mathsf{ProbeBundle}$ row, the $\mathsf{InBundle}$ membership rows,
the selected $\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the induced $\DyadicRatCore$ endpoint
rows, and the displayed $\hsame/\Cont/\Pkg$ ledger rows carried by the common
refinement.

No completion row, quotient row, host-index equality, metric-completeness row,
or off-ledger $\RealUp$ classifier is part of this visible finite-window seal
source.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-common-refinement-source-confluence}. The certified
common-refinement packet gives one StreamName source tuple for the left and
right selected windows, including the restricted finite-window classifier,
bundle membership, selected unary histories, pointwise rational classifiers,
and displayed $\hsame/\Cont/\Pkg$ provenance.

Next read both induced seal packages through
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy}. The two
$\RegSeqRat$ routes consume the same StreamName tuple and therefore present the
same accepted finite-window spine, DyadicRatCore endpoint rows, transport
ledger, and provenance to the $\RealUp$ seal boundary.

Finally use
\autoref{thm:streamname-regseqrat-realup-seal-source-minimality} for each
induced package. Minimality says that every visible source row of either seal
package is one of the displayed finite-window StreamName, $\RegSeqRat$,
DyadicRatCore, bundle, history, continuation, transport, or provenance rows.
Since the common-refinement confluence already identifies those rows, no
completion, quotient, host-index, metric-completeness, or off-ledger
$\RealUp$ classifier row can distinguish the two seal sources.
\end{proof}

\begin{theorem}[StreamName common-refinement successor projection]
\label{thm:streamname-common-refinement-successor-projection}
Let $\mathcal W_L$ and $\mathcal W_R$ be public finite-window
$\StreamNameUp$ packages over the same certified endpoint maps $s,t$, and let
$\mathcal R$ be a certified common-refinement package whose generated
$\mathsf{ProbeBundle}$ restricts to both selected windows. Let
$n:\mathsf{BHist}$ be a certified unary observation such that
$\mathsf{BHist.e1}(n)$ is an $\mathsf{InBundle}$ member of the refinement
bundle of $\mathcal R$.

Project $\mathcal R$ to the singleton successor window
$$
\mathsf{ProbeBundle.Bcons}(\mathsf{BHist.e1}(n),\mathsf{ProbeBundle.Bnil}).
$$
Reading this singleton through either selected window determines the same
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the same pointwise
$\mathsf{RatHistoryClassifier}$ row at $\mathsf{BHist.e1}(n)$, and the same
downstream source tuple consumed by the $\RegSeqRat$ handoff and by the
finite-window $\RealUp$ handoff.

The determined source tuple is the successor singleton classifier, the
singleton $\mathsf{ProbeBundle}$ membership row, the selected
$\mathsf{UnaryHistory}$ row for $n$, the pointwise rational history classifier,
and the displayed $\hsame/\Cont/\Pkg$ ledger rows inherited from
$\mathcal R$. It contains no host index equality, quotient representative,
completion data, metric row, $\RegSeqRat$ regularity row, or $\RealUp$
completeness or seal classifier.
\end{theorem}
\begin{proof}
First use
\autoref{thm:streamname-common-refinement-source-confluence}. The left route
through $\mathcal W_L$ and the right route through $\mathcal W_R$ expose one
common StreamName source tuple over $\mathcal R$, so the
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$ row and the
pointwise $\mathsf{RatHistoryClassifier}$ rows are route independent before
projection.

Next apply
\autoref{thm:streamname-successor-window-projection-determinacy} to the
$\mathsf{InBundle}$ membership row for $\mathsf{BHist.e1}(n)$. The theorem
restricts the common finite-window classifier to the singleton successor bundle
and keeps exactly the pointwise rational row indexed by that successor
observation.

Finally read the downstream boundary through
\autoref{thm:streamname-regseqrat-pointwise-handoff} and
\autoref{thm:streamname-real-regseq-obligation-separation}. These rows consume
the same successor pointwise classifier and the same displayed
$\hsame/\Cont/\Pkg$ provenance rows from either selected window, while the
$\RegSeqRat$ regularity obligation and the finite-window $\RealUp$ seal
obligation remain outside the StreamName source packet.
\end{proof}

\begin{theorem}[StreamName common-refinement source triple confluence]
\label{thm:streamname-common-refinement-source-triple-confluence}
Let $\mathcal W_1$, $\mathcal W_2$, and $\mathcal W_3$ be public
finite-window $\StreamNameUp$ packages over the same certified endpoint maps
$s,t$, and let $\mathcal R$ be a certified common-refinement package whose
generated window restricts to all three selected windows. For every pair
$(i,j)$, the route
$$
\mathcal R\longrightarrow \mathcal W_i\longrightarrow \RegSeqRat
\longrightarrow \RealUp
$$
and the route
$$
\mathcal R\longrightarrow \mathcal W_j\longrightarrow \RegSeqRat
\longrightarrow \RealUp
$$
read the same source tuple from the common refinement. That tuple is the
restricted $\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$
row, the displayed $\mathsf{ProbeBundle}$ row, the $\mathsf{InBundle}$
membership rows, the selected $\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, and the displayed
$\hsame/\Cont/\Pkg$ ledger rows carried by $\mathcal R$.

Thus the three finite-window handoffs are confluent on the source surface
used by $\RegSeqRat$ and by finite-window $\RealUp$ readback. No
$\RegSeqRat$ regularity row, seal classifier, completion data, quotient row,
metric row, or host index equality is introduced by the triple comparison.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-common-refinement-source-determinacy} to the
pairs $(\mathcal W_1,\mathcal W_2)$, $(\mathcal W_2,\mathcal W_3)$, and
$(\mathcal W_1,\mathcal W_3)$. Each application reads the two selected
windows as restrictions of the same certified common-refinement packet
$\mathcal R$.

For each pair, use
\autoref{thm:streamname-common-refinement-source-confluence}. It identifies
the downstream $\RegSeqRat/\RealUp$ source surface with the already displayed
StreamName tuple, rather than with any route-specific regularity, completion,
quotient, metric, host-index, or seal row.

The displayed common-refinement ledger is the same ledger in all three
pairwise comparisons. Transitivity of the ledger equalities for the
restricted finite-window classifier, $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, pointwise
$\mathsf{RatHistoryClassifier}$, and $\hsame/\Cont/\Pkg$ rows therefore gives
one source tuple for all three routes.
\end{proof}
