\section{StreamName Common-Refinement Public Exactness}
\label{sec:streamname-common-refinement-public-exactness}

\begin{theorem}[StreamName common-refinement public exactness]
\label{thm:streamname-common-refinement-public-exactness}
Let $\mathcal W_L$ and $\mathcal W_R$ be public finite-window $\StreamNameUp$ packages over the same certified endpoint maps $s,t$, and let $\mathcal R$ be a certified common-refinement package whose generated window restricts to both selected windows. Then every downstream $\RegSeqRat$ handoff and every finite-window $\RealUp$ handoff read from $\mathcal R$ factors through exactly the common-refinement source tuple:
$$
(\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R),
\mathsf{ProbeBundle}_{\mathcal R},
\mathsf{InBundle}_{\mathcal R},
\mathsf{UnaryHistory}_{\mathcal R},
\mathsf{RatHistoryClassifier}_{\mathcal R},
\hsame_{\mathcal R},
\Cont_{\mathcal R},
\Pkg_{\mathcal R}).
$$
The public handoff cannot add completion data, quotient rows, host-index equality, metric-completeness rows, or off-ledger $\RealUp$ classifier rows.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-common-refinement-source-determinacy}. It identifies the source tuple read from the left selected window with the source tuple read from the right selected window, because both are restrictions of the same certified common-refinement package $\mathcal R$.

Next apply \autoref{thm:streamname-common-refinement-source-confluence}. The downstream $\RegSeqRat$ route and the finite-window $\RealUp$ route receive the same restricted finite-window classifier, bundle row, membership rows, selected histories, pointwise rational classifiers, and displayed $\hsame/\Cont/\Pkg$ ledger rows.

Now use \autoref{thm:streamname-common-refinement-real-seal-confluence}. The induced $\RealUp$ seal packages have the same visible seal source, so the seal boundary cannot distinguish the two routes by adding an off-ledger classifier row.

Finally apply the RegSeqRat and RealUp handoff separation statements in the StreamName child files, in particular \autoref{thm:streamname-regseqrat-pointwise-handoff} and \autoref{thm:streamname-real-regseq-obligation-separation}. They keep regularity, completion, quotient, metric-completeness, host-index, and seal-classifier data outside the common-refinement source tuple.
\end{proof}

\begin{theorem}[StreamName common-refinement associativity]
\label{thm:streamname-common-refinement-associativity}
Let $\mathcal W_0,\mathcal W_1,\mathcal W_2$ be three compatible public finite-window $\StreamNameUp$ packages over the same certified endpoint maps. If successive common-refinement packages are displayed for both parenthesizations
$$
(\mathcal W_0 \cap \mathcal W_1) \cap \mathcal W_2
\quad\text{and}\quad
\mathcal W_0 \cap (\mathcal W_1 \cap \mathcal W_2),
$$
then the two resulting packages expose the same scheduled observation rows, $\hsame$ transports, $\Cont$ replay rows, $\Pkg$ provenance, and local $\NameCert$ row. The common-refinement read exports no completion object, quotient stream equality, host-index equality, metric-completeness row, or off-ledger $\RealUp$ classifier row.
\end{theorem}
\begin{proof}
Project each parenthesized package to its finite-window carrier. Compatibility says that every scheduled observation row is a restriction of the same three displayed windows, so either parenthesization exposes the same source rows.

Transport the common rows componentwise through the displayed $\hsame$ witnesses and replay them through the same $\Cont$ route. The $\Pkg$ provenance and local $\NameCert$ row are then read from the same finite source tuple.

Finally use common-refinement public exactness. It keeps every downstream $\RegSeqRatUp$ and $\RealUp$ handoff inside the common-refinement source tuple, so neither parenthesization can add completion, quotient, host-index, metric-completeness, or off-ledger classifier data.
\end{proof}
