\section{StreamName finite-window Real handoff coverage}
\label{sec:streamname-finite-window-real-handoff-coverage}

\begin{theorem}[StreamName finite-window Real handoff coverage]
\label{thm:streamname-finite-window-real-handoff-coverage}
Every RegSeqRat-to-$\RealUp$ handoff read mediated by $\StreamNameUp$ factors through displayed finite windows, the $\RegSeqRat$ pointwise rows, the $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows. More explicitly, the source surface is the finite inventory of $\mathsf{RatHistoryClassifier}$ observations, $\mathsf{ProbeBundle}$ ledgers, $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ observations, accepted $\RegSeqRat$ pointwise seal rows, finite continuation rows, transport rows, provenance rows, and naming rows already displayed by the StreamName handoff.

The coverage theorem exports no quotient stream, no host sequence equality, no ambient real completeness principle, no completion representative, and no $\RealUp$ seal read outside the finite StreamName and RegSeqRat rows.
\end{theorem}
\begin{proof}
First read the StreamName source surface. Apply \autoref{thm:streamname-real-regseq-finite-window-handoff}: a public StreamName handoff exposes only selected rational-history classifier rows, the finite $\mathsf{ProbeBundle}$ ledger, $\mathsf{InBundle}$ membership rows, and $\mathsf{UnaryHistory}$ observations.

Next refine that source pointwise. Apply \autoref{thm:streamname-regseqrat-pointwise-handoff}; the downstream RegSeqRat or finite-window Real consumer receives exactly the StreamName carrier rows, finite-window classifier rows, certified unary observations, membership rows, and pointwise $\hsame$ comparisons. No regularity or seal row is created by this refinement.

Now pass to the Real seal boundary. Apply \autoref{thm:streamname-real-seal-factorization-boundary}. It says that a finite-window $\RealUp$ seal read arising from the StreamName-to-RegSeqRat handoff factors through the StreamName point rows, accepted $\RegSeqRat$ seal rows, bundle and membership rows, unary observations, finite $\Cont$ ledger, displayed $\hsame$ transports, and $\Pkg$ provenance.

Finally repack the same finite rows with the local naming certificate. The cited handoff and factorization rows already supply the finite windows, pointwise RegSeqRat rows, Real seal boundary, transport, continuation, and provenance. The StreamName NameCert row names that same finite surface, so a consumer has no route to quotient streams, host sequence equality, ambient real completeness, completion representatives, or a Real seal read outside the displayed packet.
\end{proof}

\begin{theorem}[StreamName rational-ball window localization]
\label{thm:streamname-rational-ball-window-localization}
Any accepted $\StreamNameUp$ finite window used in a $\RealUp$ handoff can be localized through a displayed $\RationalIntervalUp$ containment row and then through a $\RationalBallUp$ center-radius ledger before the read reaches the $\RealUp$ seal. Conversely, a displayed $\RationalBallUp$ containment row over a $\RationalIntervalUp$ endpoint window supplies the same finite $\StreamNameUp$ observation route to the Real seal.

The localized route carries only finite $\mathsf{BHist}$ observations, interval endpoint-containment rows, ball center and nonnegative-radius rows, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows. It exports no quotient stream, host sequence equality, selected limit, ambient completeness premise, or hidden Real representative.
\end{theorem}
\begin{proof}
For the forward route, begin with \autoref{thm:streamname-finite-window-real-handoff-coverage}. It confines the handoff to a finite StreamName observation window, accepted RegSeqRat pointwise rows, the Real seal boundary, transport rows, continuation rows, provenance, and local naming rows.

Refine that finite observation window through the endpoint discipline of \autoref{ch:concrete-instances-rationalinterval-namecert}. The interval row supplies the displayed containment boundary for the rational observations without adding a completed real, quotient stream, or host equality.

Now pass from the interval row to the ball ledger of \autoref{ch:concrete-instances-rational-ball-namecert}. The center row, nonnegative-radius row, and containment ledger localize the same observations by a finite rational-radius packet before the handoff reaches the Real seal.

For the converse route, start from the displayed $\RationalBallUp$ containment row over a displayed $\RationalIntervalUp$ endpoint window. Reading the center-radius ledger back through the interval containment row gives the same finite rational observation packet. Applying the StreamName coverage theorem again routes that packet through the same finite StreamName observation rows and then to the $\RealUp$ seal, with all excluded quotient, host, selected-limit, and completeness coordinates still absent.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real window factorization]
\label{thm:streamname-regseqrat-real-window-factorization}
Suppose two $\StreamNameUp$-mediated $\RegSeqRat$-to-$\RealUp$ handoff reads use the same finite StreamName window, the same accepted $\RegSeqRat$ pointwise row, and the same $\RealUp$ seal boundary. Then the two reads have the same public source surface: the same finite packet of $\mathsf{RatHistoryClassifier}$ observations, $\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, $\mathsf{UnaryHistory}$ observations, $\RegSeqRat$ pointwise seal rows, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

This factorization exposes no second $\RealUp$ seal, no quotient stream, no host sequence equality, no selected completion representative, and no ambient completeness coordinate.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-window-real-handoff-coverage} to both handoff reads. The two inventories are finite packets whose only public rows are the StreamName window, the RegSeqRat pointwise data, the Real seal boundary, the displayed transport and continuation routes, the provenance row, and the local naming rows.

Next apply \autoref{thm:streamname-regseqrat-pointwise-handoff} to the shared accepted pointwise row. It identifies the RegSeqRat portion of both packets with the same StreamName carrier rows, classifier observations, unary observations, membership rows, and componentwise $\hsame$ comparisons.

Now apply \autoref{thm:streamname-real-seal-factorization-boundary} to the shared Real seal boundary. The Real read factors through the same accepted RegSeqRat rows, finite bundle rows, displayed $\Cont$ routes, $\Pkg$ provenance, and transport rows; it does not create an additional Real-facing source coordinate.

Finally use \autoref{thm:streamname-real-regseq-common-window-consumer-determinacy}. Common-window determinacy identifies the two consumer reads once their finite StreamName window, RegSeqRat row, and Real seal boundary agree. Repacking those common rows under the local $\NameCert$ surface gives the stated public packet and rules out any quotient, host-equality, representative, or ambient-completeness exposure.
\end{proof}

\begin{theorem}[StreamName Real handoff pullback exactness]
\label{thm:streamname-real-handoff-pullback-exactness}
A public $\RealUp$ seal read mediated by $\StreamNameUp$ and $\RegSeqRat$ is accepted exactly when it factors through the finite $\StreamNameUp$ window, the accepted $\RegSeqRat$ pointwise row, the $\RealUp$ seal boundary, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows. No accepted read may replace that pullback surface by quotient streams, host sequence equality, completion representatives, or ambient real completeness.
\end{theorem}
\begin{proof}
For the forward direction, start from an accepted public $\RealUp$ seal read. Apply \autoref{thm:streamname-finite-window-real-handoff-coverage} to expose the finite StreamName window, accepted RegSeqRat pointwise rows, Real seal boundary, transport rows, continuation rows, provenance, and local naming rows.

Next apply \autoref{thm:streamname-regseqrat-real-window-factorization}. It identifies the public source surface of the read with the same finite StreamName window, the same accepted RegSeqRat pointwise row, and the same Real seal boundary before any downstream Real consumer can read the packet.

Now apply \autoref{thm:streamname-real-seal-factorization-boundary}. The Real-facing row is therefore reached only through the displayed handoff surface: finite StreamName observations, RegSeqRat pointwise acceptance, the seal boundary, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ rows.

For the reverse direction, suppose such a finite pullback surface is displayed. Repack the listed rows as the StreamName-mediated RegSeqRat-to-Real handoff packet. The coverage theorem accepts exactly that inventory, the window factorization identifies the public source surface, and the Real seal factorization supplies the downstream seal route.

The excluded objects remain outside both directions. Quotient streams, host sequence equality, completion representatives, and ambient real completeness are not coordinates of the displayed pullback surface, so neither acceptance nor reconstruction can cite them.
\end{proof}

\begin{theorem}[StreamName finite-window budget monotonicity]
\label{thm:streamname-finite-window-budget-monotonicity}
Let $P \leq Q$ be finite observation budgets for two $\StreamNameUp$-mediated $\RegSeqRat$-to-$\RealUp$ handoff reads. Suppose the $Q$-budget packet restricts on $P$ to the same selected StreamName rows, the same accepted $\RegSeqRat$ pointwise row, and the same $\RealUp$ seal boundary as the $P$-budget packet. Then enlarging the budget from $P$ to $Q$ preserves the downstream $\RealUp$ seal consumer's public source surface.

The preserved surface consists only of finite $\mathsf{BHist}$ observations, $\mathsf{ProbeBundle}$ rows, $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ observations, pointwise $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows visible in the restricted packet. The monotone handoff exports no quotient stream, no host sequence equality, no selected limit, and no ambient completeness principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-finite-window-real-handoff-coverage} to the $P$-budget handoff and to the $Q$-budget handoff. Both consumers are therefore confined to finite StreamName, RegSeqRat, Real-boundary, transport, continuation, provenance, and local naming rows.

Use \autoref{thm:streamname-regseqrat-pointwise-handoff} on the restriction of the $Q$ packet to $P$. The hypothesis identifies the selected StreamName rows and the accepted pointwise RegSeqRat row with the $P$ packet, so the componentwise $\hsame$ and unary-history coordinates read by the Real consumer are the same on the restricted window.

Next apply \autoref{thm:streamname-real-seal-factorization-boundary}. The RealUp seal still factors through the displayed finite route: bundle membership, accepted RegSeqRat rows, displayed $\Cont$ rows, $\Pkg$ provenance, and the local transport rows. The larger budget supplies no additional seal-facing coordinate once its restriction has the same boundary row.

Finally apply \autoref{thm:streamname-regseqrat-real-window-factorization} to the shared restricted window. It identifies the public source surface seen by the downstream RealUp seal consumer, and the identified surface contains exactly the finite BEDC rows named in the statement. Quotient streams, host sequence equality, selected limits, and ambient completeness remain outside the handoff packet.
\end{proof}

\begin{theorem}[StreamName Real-RegSeq common-window lattice coherence]
\label{thm:streamname-real-regseq-window-lattice-coherence}
Suppose two $\StreamNameUp$-mediated $\RegSeqRat$-to-$\RealUp$ handoff reads are compared through a certified common finite-window lattice meet. If their accepted $\RegSeqRat$ pointwise rows and their $\RealUp$ seal boundary agree on that meet, then both reads expose the same finite $\mathsf{BHist}$ source surface. The common surface consists exactly of the $\mathsf{RatHistoryClassifier}$ observations, $\mathsf{ProbeBundle}$ rows, $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ observations, accepted $\RegSeqRat$ pointwise seal rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows carried by the meet packet.

This lattice coherence statement exports no quotient stream equality, no host sequence equality, no ambient $\RealUp$ completeness, no selected completion representative, and no metric-completeness row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-window-real-handoff-coverage} to each handoff read. Each read is already confined to the finite StreamName window, accepted RegSeqRat pointwise rows, the Real seal boundary, transport rows, continuation rows, provenance, and local naming rows.

Next apply \autoref{thm:streamname-regseqrat-real-window-factorization}. The assumed agreement of the accepted pointwise rows and the Real seal boundary identifies the RegSeqRat and Real-facing rows that both reads can expose over the same window.

Now use \autoref{thm:streamname-finite-window-lattice-meet-exhaustion}. The certified meet is a shared finite observation packet, so every RegSeqRat consumer and every finite-window RealUp consumer reads only its classifier, bundle, membership, unary-history, dyadic ledger, transport, continuation, provenance, and local naming coordinates.

Finally apply \autoref{thm:streamname-real-regseq-common-window-consumer-determinacy}. Common-window determinacy identifies the consumer reads on the certified meet surface. Repacking that identified surface gives the same finite $\mathsf{BHist}$ source packet for both handoffs and leaves quotient equality, host sequence equality, ambient Real completeness, selected representatives, and metric-completeness rows outside the public lattice surface.
\end{proof}

\begin{theorem}[StreamName Real seal observation-budget factorization]
\label{thm:streamname-real-seal-observation-budget-factorization}
Any finite-window $\StreamNameUp$ packet whose read is consumed by $\RegSeqRatUp$ and sealed as $\RealUp$ factors through the displayed observation-budget limiter route whenever an accepted $\ObservationBudgetLimiterUp$ packet is present. The common route is the request row, budget row, cap row, window row, dyadic ledger, $\RegSeqRat$ readback, $\RealUp$ seal, and structural rows named by the limiter surface of \autoref{ch:concrete-instances-observation-budget-limiter-namecert}.

This factorization exports no uncapped schedule, hidden selector, quotient stream, host real equality, selected limit, independent real carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with the finite-window handoff coverage. By \autoref{thm:streamname-finite-window-real-handoff-coverage}, the StreamName-to-Real route already exposes only finite StreamName observations, RegSeqRat pointwise rows, the Real seal boundary, transport rows, continuation rows, provenance, and local naming rows.

Refine the route through \autoref{thm:streamname-regseqrat-real-window-factorization}. The RegSeqRat readback and Real seal have the same public source surface whenever the finite window, accepted pointwise row, and seal boundary agree.

Now use \autoref{thm:streamname-real-regseq-window-lattice-coherence}. The common-window lattice pins the classifier observations, bundle rows, membership rows, unary-history observations, dyadic ledger, transports, routes, provenance, and local names to one finite observation packet.

When an accepted $\ObservationBudgetLimiterUp$ packet is present, its request, budget, cap, and window rows are exactly the displayed limiter boundary through which that finite observation packet is read. Since neither the StreamName handoff nor the limiter carrier contains an uncapped schedule, hidden selector, quotient stream, host real equality, selected limit, independent real carrier, or ambient completeness coordinate, none of those objects can be exported by the factorization.
\end{proof}

\begin{theorem}[StreamName Real observation-budget route]
\label{thm:streamname-real-observation-budget-route}
Any finite-window $\StreamNameUp$ packet consumed by $\RegSeqRatUp$ and sealed as $\RealUp$, when read by a $\RealObservationBudgetUp$ consumer, factors through the request, budget, and window route of \autoref{ch:concrete-instances-real-observation-budget-namecert}. The route first exposes the finite StreamName surface, the $\RegSeqRat$ pointwise row, and the $\RealUp$ seal boundary, and then repacks them as the $\RealObservationBudgetUp$ packet
$$
E,W,D,R,S,H,C,P,N
$$
over the precision request, selected finite windows, dyadic readbacks and radii, $\RegSeqRatUp$ handoff rows, $\RealUp$ seal rows, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.

This route exports no uncapped schedule, quotient stream, host sequence equality, selected limit, independent real carrier, ambient completeness principle, or host real equality.
\end{theorem}
\begin{proof}
Begin with the finite-window handoff coverage. By \autoref{thm:streamname-finite-window-real-handoff-coverage}, the StreamName-to-Real packet already exposes only finite StreamName observations, $\RegSeqRat$ pointwise rows, the $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

Next apply \autoref{thm:streamname-regseqrat-real-window-factorization}. It identifies the public source surface of the consumed packet with the same finite StreamName window, the same accepted $\RegSeqRat$ pointwise row, and the same $\RealUp$ seal boundary before the observation-budget consumer reads it.

Now use \autoref{thm:streamname-real-regseq-window-lattice-coherence}. The common finite-window lattice pins the classifier observations, bundle rows, membership rows, unary-history observations, dyadic ledger, transports, routes, provenance, and local names to one finite observation packet.

Apply \autoref{thm:streamname-real-seal-observation-budget-factorization} to pass that packet through the displayed observation-budget limiter boundary. The limiter supplies the request, budget, cap, and window discipline needed before a bounded real-facing consumer can inspect the StreamName handoff.

Finally route the bounded packet through \autoref{ch:concrete-instances-real-observation-budget-namecert}. Its carrier \autoref{def:real-observation-budget-carrier} and non-escape theorem \autoref{thm:real-observation-budget-nonescape} repack the same finite surface as $E,W,D,R,S,H,C,P,N$, with componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and the local $\NameCert_{\RealObservationBudgetUp}$ row. Since neither the source handoff nor the observation-budget carrier contains an uncapped schedule, quotient stream, host sequence equality, selected limit, independent real carrier, ambient completeness row, or host real equality row, the routed consumer cannot export any of those objects.
\end{proof}

\begin{theorem}[StreamName Real terminal factorization]
\label{thm:streamname-real-terminal-factorization}
Any finite-window $\StreamNameUp$ packet consumed by $\RegSeqRatUp$, sealed as $\RealUp$, and then read by a Real-facing consumer factors through the terminal source lock of \autoref{def:streamname-regseqrat-realup-terminal-source-lock}. The common terminal packet is exactly the finite $\BHist$ window, accepted $\RegSeqRat$ pointwise row, induced $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.

The factorization exports no quotient stream, host sequence equality, selected limit, ambient real completeness, independent Real carrier, or metric-completeness row.
\end{theorem}
\begin{proof}
First project the finite StreamName rows. By \autoref{thm:streamname-finite-window-real-handoff-coverage}, the handoff read exposes only finite classifier observations, bundle and membership rows, unary observations, pointwise $\RegSeqRat$ rows, the $\RealUp$ seal boundary, transport rows, continuation rows, provenance, and local naming rows.

Next identify the public source surface by \autoref{thm:streamname-regseqrat-real-window-factorization}. The finite StreamName window, accepted $\RegSeqRat$ pointwise row, and $\RealUp$ seal boundary determine the same surface for every downstream Real-facing read.

Apply \autoref{thm:streamname-real-handoff-pullback-exactness}. The accepted read is therefore a pullback over exactly the finite window, pointwise row, seal boundary, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

Now route the bounded consumer through \autoref{thm:streamname-real-observation-budget-route}. The Real-facing observation request reads the same finite packet through $\RealObservationBudgetUp$, so the request, budget, and window discipline do not introduce an additional source coordinate.

Finally apply \autoref{thm:streamname-regseqrat-realup-terminal-source-lock}. The terminal lock identifies the common source surface with the lock packet of \autoref{def:streamname-regseqrat-realup-terminal-source-lock}: the finite $\BHist$ window, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows together with the accepted $\RegSeqRat$ and induced $\RealUp$ seal rows. Since none of the cited routes carries quotient streams, host sequence equality, selected limits, ambient completeness, an independent Real carrier, or metric-completeness data, none is exported by the terminal factorization.
\end{proof}

\begin{theorem}[StreamName Real terminal quotient refusal]
\label{thm:streamname-real-terminal-quotient-refusal}
Any finite-window $\StreamNameUp$ packet consumed by $\RegSeqRatUp$, sealed as $\RealUp$, and then read by a $\QuotientStreamRefusalUp$ consumer factors first through the terminal source lock of \autoref{def:streamname-regseqrat-realup-terminal-source-lock} and then through the refusal ledger of the $\QuotientStreamRefusalUp$ route. The source-facing part of the read is exactly the finite $\BHist$ window, accepted $\RegSeqRat$ pointwise row, induced $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row already locked by the terminal source packet.

Requests for quotient stream equality, host sequence equality, selected limits, hidden tail oracles, ambient completeness, or metric-completeness rows are routed to refusal rather than exported as completion coordinates.
\end{theorem}
\begin{proof}
Start with the terminal factorization. By \autoref{thm:streamname-real-terminal-factorization}, every Real-facing read of the finite StreamName-to-RegSeqRat-to-Real packet has the common source surface consisting only of the finite window, accepted pointwise row, induced seal row, componentwise transport, displayed continuation, provenance, and local naming rows.

Identify that source surface with the explicit lock packet of \autoref{def:streamname-regseqrat-realup-terminal-source-lock}. The lock contains no quotient stream, host sequence equality, selected limit, hidden tail oracle, ambient completeness row, independent Real carrier, or metric-completeness coordinate, so none of those objects is available before the refusal consumer is consulted.

Now pass the locked packet to the $\QuotientStreamRefusalUp$ consumer. Apply \autoref{thm:quotient-stream-refusal-nonescape-route}: a completion-facing request that leaves the displayed finite route is sent to the refusal row and exports no completion coordinate.

Finally use \autoref{thm:quotient-stream-refusal-terminal-route-exhaustion}. The terminal refusal route exhausts the accepted read by the displayed route and refusal rows, with transport, replay, provenance, and naming attached to that route. Thus the StreamName terminal packet reaches the refusal ledger, while quotient equality, host equality, selected limits, hidden tail data, ambient completeness, and metric-completeness rows remain refused rather than exported.
\end{proof}
