\begin{theorem}[StreamNameUp finite-window cover-refinement classifier]
\label{thm:streamname-finite-window-cover-refinement-classifier}
For certified observation maps $s,t:\Hist\to\Hist$ and probe bundles
$\mathcal{P}_1,\mathcal{P}_2,\mathcal{Q}:\mathsf{ProbeBundle}$, suppose
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P}_1)
\quad\text{and}\quad
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P}_2).
$$
Assume every requested bundled unary observation of $\mathcal{Q}$ is covered
by one of the two certified windows:
$$
\forall n,\ \mathsf{InBundle}(n,\mathcal{Q})\to
\mathsf{UnaryHistory}(n)\to
\mathsf{InBundle}(n,\mathcal{P}_1)\lor
\mathsf{InBundle}(n,\mathcal{P}_2).
$$
Then the requested window is certified:
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{Q}).
$$
Moreover, for any selected $n$ in $\mathcal{Q}$ with
$\mathsf{UnaryHistory}(n)$ and displayed one-extension endpoints
$$
\hsame(s(n),\Eone(a))\quad\text{and}\quad \hsame(t(n),\Eone(b)),
$$
the selected observation carries the full endpoint package of
\autoref{thm:rat-stream-name-finite-window-selected-full-endpoint-package}.
\end{theorem}
\begin{proof}
First combine the two certified windows. The union clause of
\autoref{thm:rat-stream-name-finite-window-structural-laws} repacks the
$\mathcal{P}_1$ and $\mathcal{P}_2$ classifiers as a classifier on the
displayed union bundle.

Next restrict the union classifier to the requested bundle. For a bundled
unary observation $n$ of $\mathcal{Q}$, the cover hypothesis chooses whether
the membership row comes from $\mathcal{P}_1$ or from $\mathcal{P}_2$. In
either case the corresponding inclusion into the displayed union bundle gives
the subwindow map required by the subwindow clause of
\autoref{thm:rat-stream-name-finite-window-structural-laws}. This yields
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{Q}).
$$

Finally fix a selected requested observation $n$ together with its bundle
membership, unary witness, and displayed one-extension endpoints. Apply
\autoref{thm:rat-stream-name-finite-window-selected-full-endpoint-package} to
the $\mathcal{Q}$ classifier just constructed. The resulting point classifier,
positive-denominator rows, unary endpoint rows, empty and zero-headed
exclusions, and one-tail readback are exactly the full endpoint package for
the requested observation.
\end{proof}

\begin{theorem}[StreamName cover-refinement transport closure]
\label{thm:streamname-cover-refinement-transport-closure}
For certified observation maps $s,t,s',t':\Hist\to\Hist$ and probe bundles
$\mathcal{P}_1,\mathcal{P}_2,\mathcal{Q}:\mathsf{ProbeBundle}$, suppose
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P}_1)
\quad\text{and}\quad
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P}_2).
$$
Assume every requested bundled unary observation of $\mathcal{Q}$ is covered
by one of the two certified windows:
$$
\forall n,\ \mathsf{InBundle}(n,\mathcal{Q})\to
\mathsf{UnaryHistory}(n)\to
\mathsf{InBundle}(n,\mathcal{P}_1)\lor
\mathsf{InBundle}(n,\mathcal{P}_2).
$$
Assume also that the endpoints are transported componentwise on every bundled
unary observation of $\mathcal{Q}$:
$$
\forall n,\ \mathsf{InBundle}(n,\mathcal{Q})\to
\mathsf{UnaryHistory}(n)\to\hsame(s(n),s'(n))
$$
and
$$
\forall n,\ \mathsf{InBundle}(n,\mathcal{Q})\to
\mathsf{UnaryHistory}(n)\to\hsame(t(n),t'(n)).
$$
Then
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s',t',\mathcal{Q}).
$$
Moreover, for every selected $n$ in $\mathcal{Q}$ with
$\mathsf{UnaryHistory}(n)$ and histories $a,b:\Hist$ displaying transported
one-extension endpoints
$$
\hsame(s'(n),\Eone(a))\quad\text{and}\quad \hsame(t'(n),\Eone(b)),
$$
the selected observation exports the same finite endpoint package to the
$\RegSeqRat$ and $\RealUp$ handoff surface: the selected point classifier,
positive-denominator rows, unary endpoint rows, empty and zero-headed
exclusions, one-tail readback, $\mathsf{InBundle}$ membership, bundled
$\mathsf{UnaryHistory}$ row, finite $\Cont$ ledger, displayed $\hsame$
transports, and $\mathsf{Pkg}$ provenance. No host index, quotient
representative, completion object, metric row, or $\RealUp$ completeness datum
is introduced.
\end{theorem}
\begin{proof}
First build the classifier on the requested cover. Apply
\autoref{thm:streamname-finite-window-cover-refinement-classifier} to the two
certified windows and to the displayed cover of $\mathcal{Q}$. This gives
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{Q}).
$$

Next transport that classifier along the endpoint rows over $\mathcal{Q}$.
The endpoint-transport field of
\autoref{thm:rat-stream-name-finite-window-stability-fields} applies
componentwise to the two displayed $\hsame$ transport families, yielding
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s',t',\mathcal{Q}).
$$

Finally fix a selected bundled unary observation and its displayed transported
one-extension endpoints. Apply
\autoref{thm:rat-stream-name-finite-window-selected-full-endpoint-package} to
the transported classifier. The resulting selected endpoint package is the
finite package consumed by the downstream surface, and
\autoref{thm:streamname-real-seal-factorization-boundary} records that this
surface factors only through the listed StreamName, $\RegSeqRat$,
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
$\Cont$, $\hsame$, and $\mathsf{Pkg}$ rows.
\end{proof}

\begin{theorem}[StreamName cover-refinement Real seal source invariance]
\label{thm:streamname-cover-refinement-real-seal-source-invariance}
For certified observation maps $s,t,s',t':\Hist\to\Hist$ and probe bundles
$\mathcal{P}_1,\mathcal{P}_2,\mathcal{Q}:\mathsf{ProbeBundle}$, assume the
two-window cover hypotheses for $\mathcal{P}_1$, $\mathcal{P}_2$, and
$\mathcal{Q}$ from
\autoref{thm:streamname-cover-refinement-transport-closure}, together with
the same componentwise endpoint transports from $s,t$ to $s',t'$ over
$\mathcal{Q}$. Then every downstream finite-window $\RealUp$ seal read over
$\mathcal{Q}$ reads the same $\StreamNameUp$ source surface after refinement.

That invariant surface consists exactly of the finite-window classifier, the
selected $\mathsf{ProbeBundle}$ row, $\mathsf{InBundle}$ membership,
$\mathsf{UnaryHistory}$, the pointwise $\RatHistoryClassifier$, displayed
$\hsame$ transports, the $\Cont$ ledger, and $\mathsf{Pkg}$ provenance. No
host index, quotient representative, completion object, metric row, or
external $\RealUp$ completeness datum becomes available under the covered
refinement.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-finite-window-cover-refinement-classifier} to the
two certified windows and the displayed cover of $\mathcal{Q}$. This builds
the finite-window classifier on the requested probe bundle using only the
already certified source rows.

Next apply
\autoref{thm:streamname-cover-refinement-transport-closure}. The
componentwise endpoint transports carry the classifier to $s',t'$ and keep the
selected endpoint package on the same $\mathcal{Q}$ bundle, with its
$\mathsf{InBundle}$ membership, $\mathsf{UnaryHistory}$ row, point classifier,
$\Cont$ ledger, displayed $\hsame$ rows, and $\mathsf{Pkg}$ provenance.

Finally pass to the $\StreamNameUp$ Real--$\RegSeqRat$ handoff and the
$\RealUp$ seal factorization boundary. Those results identify exactly the
consumer rows available to a finite-window seal read, so the refinement can
transport the source surface but cannot add a host index, quotient
representative, completion object, metric row, or external completeness
datum.
\end{proof}
