\begin{theorem}[StreamName finite-window pointwise reflexivity]
\label{thm:streamname-finite-window-pointwise-reflexivity}
Let $s:\Hist\to\Hist$ be an accepted rational StreamName carrier and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be a certified finite bundle of unary
observations. Then the restriction of $s$ to $\mathcal{P}$ carries the
pointwise rows
$$
\mathsf{InBundle}(n,\mathcal{P})\to
\mathsf{UnaryHistory}(n)\to
\mathsf{RatHistoryClassifier}(s(n),s(n))
$$
and repacks as the finite-window self-witness
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,s,\mathcal{P}).
$$
The witness exposes only the displayed $\mathsf{UnaryHistory}$ observations,
bundle-membership rows, endpoint rational-history carrier rows, pointwise
RatUp reflexivity, $\hsame$ transports already present on the window,
displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ rows.
It contains no quotient stream, host sequence equality, selected limit, or
$\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Unfold the carrier clause of Definition~\ref{def:rat-stream-name-carrier}.
For a bundled certified unary observation $n$, the accepted carrier of $s$
supplies the endpoint rational-history carrier row
$\mathsf{RatHistoryCarrier}(s(n))$.

Apply the reflexivity field of
\autoref{thm:rat-stream-name-certificate-fields} pointwise at this same
observation. Equivalently, the RatUp classifier reflexivity row turns the
projected endpoint carrier into
$\mathsf{RatHistoryClassifier}(s(n),s(n))$.

Since $n$ was chosen with arbitrary evidence
$\mathsf{InBundle}(n,\mathcal{P})$ and $\mathsf{UnaryHistory}(n)$, the
pointwise rows are exactly the clauses of
Definition~\ref{def:rat-stream-name-finite-window-classifier}. Repacking them
therefore gives
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,s,\mathcal{P})$.

The surrounding handoff surface is unchanged. The finite bundle contributes
only membership, unary-history, displayed transport, continuation, provenance,
and naming rows, so the same finite-window self-witness is the local source
row consumed by
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff} and by the
$\RealUp$ finite-window boundary without importing quotient-stream equality,
host sequence equality, selected limits, or completeness data.
\end{proof}

\begin{theorem}[StreamName finite-window pointwise symmetry]
\label{thm:streamname-finite-window-pointwise-symmetry}
Let $s,t:\Hist\to\Hist$ be accepted rational StreamName carriers and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be a certified finite bundle of unary
observations. If
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})$ holds, then
the same displayed bundle rows, unary observations, endpoint carrier rows,
pointwise RatUp symmetry, $\hsame$ transports, $\Cont$ routes, $\Pkg$
provenance, and local $\NameCert$ rows repack as
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(t,s,\mathcal{P}).
$$
The repacked classifier contains no quotient stream, host sequence equality,
selected limit, or $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:rat-stream-name-finite-window-classifier}. A
bundled certified unary observation $n$ supplies the same membership evidence
$\mathsf{InBundle}(n,\mathcal{P})$, the same unary-history witness, and the two
endpoint rational-history carrier rows already exposed by the source finite
window.

At this observation, apply the symmetry field of
\autoref{thm:rat-stream-name-certificate-fields} to the displayed pointwise
RatUp classifier row
$\mathsf{RatHistoryClassifier}(s(n),t(n))$. This yields the reversed point
classifier $\mathsf{RatHistoryClassifier}(t(n),s(n))$ without changing the
finite bundle or the endpoint carriers.

Since the observation and bundle-membership evidence were arbitrary, the
reversed pointwise rows satisfy exactly the clauses of
Definition~\ref{def:rat-stream-name-finite-window-classifier} for the ordered
pair $(t,s)$. Repack them with the unchanged $\hsame$ transports, $\Cont$
routes, $\Pkg$ provenance, and local $\NameCert$ rows.

All data remain finite-window data. No quotient stream, host sequence equality,
selected limit, or $\RealUp$ completeness witness is read or introduced.
\end{proof}

\begin{theorem}[StreamName finite-window pointwise transitivity]
\label{thm:streamname-finite-window-pointwise-transitivity}
Let $s,t,u:\Hist\to\Hist$ be accepted rational StreamName carriers and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be a certified finite bundle of unary
observations. If
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})$ and
$\mathsf{RatStreamNameFiniteWindowClassifier}(t,u,\mathcal{P})$ hold over this
same finite bundle, then the displayed finite-window rows compose pointwise to
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,u,\mathcal{P}).
$$
The composition uses only pointwise RatUp transitivity and the displayed
finite-window rows; it adds no quotient stream, host sequence equality,
selected limit, or $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:rat-stream-name-finite-window-classifier} for the
two source windows. A bundled certified unary observation $n$ in
$\mathcal{P}$ reads a point classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ from the first window and a point
classifier $\mathsf{RatHistoryClassifier}(t(n),u(n))$ from the second.

Apply the transitivity field of
\autoref{thm:rat-stream-name-certificate-fields} at this same observation. The
middle endpoint carrier row is the displayed $t(n)$ row already shared by the
two windows, so the RatUp point classifiers compose to
$\mathsf{RatHistoryClassifier}(s(n),u(n))$.

Because both hypotheses use the same finite bundle $\mathcal{P}$, no
membership transport or window refinement is needed. The composed pointwise
rows therefore satisfy exactly the clauses of
Definition~\ref{def:rat-stream-name-finite-window-classifier} for $(s,u)$.

Repack the unchanged bundle-membership rows, unary observations, endpoint
carrier rows, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local
$\NameCert$ rows. The resulting witness remains a finite-window classifier and
does not import quotient-stream equality, host sequence equality, selected
limits, or completeness data.
\end{proof}
