\section{Finite Observation Section Cofinality}
\label{sec:streamname-finite-observation-section-cofinality}

\begin{theorem}[StreamName finite observation section cofinality]
\label{thm:streamname-finite-observation-section-cofinality}
Every finite observation request on a pointwise certified $\StreamNameUp$ source factors through a finite section window that is cofinal for $\RegSeqRatUp$ and $\RealUp$ handoff reads. Concretely, after the request opens its index ledger, certified source row, finite $\BHist$ window, pointwise classifier row, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, any later regular-rational or real-seal consumer may refine the request only by another finite section window over the same StreamName source. The handoff exposes finite BHist, hsame, Cont, and Pkg rows rather than quotient stream equality, selected limits, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-pointwise-classifier-stability}. It keeps every accepted pointwise classifier read attached to the requested index ledger, certified source row, opened $\BHist$ window, transport row, replay row, provenance row, and local naming row.

Use \autoref{thm:streamname-pointwise-certified-source-constant-section} for the section shape. The finite request section is the row package visible to $\RegSeqRatUp$ and $\RealUp$ consumers before either consumer can read a constant or regular point stream.

Now pass to the RegSeqRat and Real handoff files already carried by the StreamName hub. Their handoff reads consume finite windows and terminal seal rows through the same displayed StreamName source, so a larger downstream request is represented by a finite refinement of the same section window.

Thus the finite section windows are cofinal for the L10 handoff route. Since each step is expressed through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, no quotient stream equality, selected limit, host real equality, or ambient completeness principle is introduced.
\end{proof}

\begin{theorem}[StreamName finite observation section public cofinality]
\label{thm:streamname-finite-observation-section-public-cofinality}
Every public $\RegSeqRatUp$ or $\RealUp$ handoff read through $\StreamNameUp$ factors through the finite observation section package of \autoref{thm:streamname-finite-observation-section-cofinality}. Any later refinement remains a finite section refinement over the same certified StreamName source, with the same index ledger, finite $\BHist$ window, pointwise classifier row, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row.

The public handoff surface therefore exports finite sections only. It contains no quotient stream equality, selected limit, countable-choice row, host real equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with finite observation section cofinality, \autoref{thm:streamname-finite-observation-section-cofinality}. It already states that finite observation requests cofinally cover the RegSeqRat and Real handoff reads over the displayed StreamName source.

Apply pointwise classifier stability, \autoref{thm:streamname-pointwise-classifier-stability}. The classifier row, finite $\BHist$ window, transport row, replay row, provenance row, and local naming row remain attached to the same source when the handoff is refined.

The RegSeqRat and Real handoff inputs consume exactly those finite section rows before reading regular rational or real-seal data. Hence a public handoff cannot bypass the finite observation package; it may only request a larger finite section over the same source.

Since the route never introduces quotient streams, selected limits, countable choice, host real equality, or ambient completeness, the public cofinality interface is the same finite-section interface already witnessed locally.
\end{proof}
