\section{StreamName finite-window budget handoff}
\label{sec:streamname-real-regseq-finite-window-budget-handoff}

\begin{theorem}[StreamName Real RegSeq finite-window budget handoff]
\label{thm:streamname-real-regseq-finite-window-budget-handoff}
Let $\mathcal W$ be an accepted finite $\StreamNameUp$ package consumed by a
$\RegSeqRatUp$ certificate, by a finite-window $\RealUp$ seal route, or by a
route that passes through a $\RegularCauchyTailBudgetUp$ or
$\ObservationBudgetLimiterUp$ packet. Then any consumer-visible regularity
row, dyadic tolerance row, or $\RealUp$ seal row must be downstream of the same
finite observation-budget surface:
$$
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory},\quad \ObservationBudgetLimiterUp,\quad
\RegularCauchyTailBudgetUp.
$$
Thus the StreamName handoff first exposes the finite window, membership,
unary-history, budget-limiter, and tail-budget rows before any RegSeqRat
regularity, dyadic tolerance, or Real seal row is consumed.

The handoff exports no quotient stream, selected host limit, countable-choice
selector, or host real equality.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-real-regseq-finite-window-handoff}. The
public StreamName package exports only selected rational-history classifier
rows, the finite $\mathsf{ProbeBundle}$ ledger, $\mathsf{InBundle}$ membership
rows, and $\mathsf{UnaryHistory}$ observation rows to a $\RegSeqRatUp$ or
finite-window $\RealUp$ consumer.

Next apply
\autoref{thm:streamname-real-regseq-obligation-separation}. It places
regularity and dyadic-tolerance rows on the $\RegSeqRatUp$ side and the seal
classifier on the $\RealUp$ side, so none of those rows can be consumed as
StreamName source data.

Now route the same finite observation surface through the sibling budget
chapters. The limiter factorization
\autoref{thm:observation-budget-limiter-cauchy-tail-budget-factorization}
forces any $\RegularCauchyTailBudgetUp$ use of the limiter row through the
request-budget-cap service triad before tail windows, dyadic observations,
readback, and seal rows are served.

Finally use
\autoref{thm:regular-cauchy-tail-budget-observation-gate}. It orders the
regular source, tail threshold, observation limiter, finite StreamName window,
dyadic ledger, RegSeqRat readback, and Real seal as one finite route. Since
the cited StreamName, limiter, and tail-budget surfaces contain no coordinates
for quotient streams, selected host limits, countable choice, or host real
equality, those objects cannot be alternate sources for the handoff.
\end{proof}

\begin{theorem}[StreamName budget handoff sibling chapter route]
\label{thm:streamname-budget-handoff-sibling-chapter-route}
Every accepted finite $\StreamNameUp$ window consumed through the finite
observation-budget surface factors through the sibling chapter surface of
\autoref{ch:concrete-instances-observationbudgetlimiter-namecert} before the
tail-budget service of
\autoref{ch:concrete-instances-regular-cauchy-tail-budget-namecert}. Its
consumer-visible route then passes through the $\RegSeqRatUp$ readback and
$\RealUp$ seal rows already named in
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff}. No accepted
finite StreamName handoff obtains an alternate source for quotient streams,
selected host limits, countable choice, or host real equality.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-real-regseq-finite-window-budget-handoff} to the
accepted finite StreamName window. It already identifies the finite observation
surface that must be exposed before any $\RegSeqRatUp$ regularity,
dyadic-tolerance, or $\RealUp$ seal row is consumed.

Next read the limiter leg through
\autoref{thm:observation-budget-limiter-cauchy-tail-budget-factorization}. The
factorization places the handoff on the
\ObservationBudgetLimiterUp\ request-budget-cap service triad before any
$\RegularCauchyTailBudgetUp$ tail window, dyadic observation, readback, or seal
row can be served.

Finally use \autoref{thm:regular-cauchy-tail-budget-observation-gate}. It orders
the tail-budget route through the regular source, tail threshold, observation
limiter, finite StreamName window, dyadic ledger, RegSeqRat readback, and Real
seal. The non-escape sentence in
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff} therefore
applies to the whole sibling chapter route.
\end{proof}

\begin{theorem}[StreamName regular seal sibling route]
\label{thm:streamname-regular-seal-sibling-route}
Any finite $\StreamNameUp$ window routed through $\ObservationBudgetLimiterUp$
and $\RegularCauchyTailBudgetUp$ reaches a $\RealUp$ finite-window seal only
through the same rows used by
\autoref{thm:streamname-finite-window-regularity-real-seal-nonescape}:
$$
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory},\quad \RegSeqRatUp,\quad \DyadicRatCoreUp,\quad
\hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
The sibling route exports no quotient stream, selected host limit,
countable-choice selector, host real equality, metric completeness, or ambient
$\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-real-regseq-finite-window-budget-handoff}. It
places every finite-window regularity, dyadic tolerance, and Real seal read
behind the finite observation-budget surface.

Use \autoref{thm:streamname-budget-handoff-sibling-chapter-route} to pass that
surface through the $\ObservationBudgetLimiterUp$ and
$\RegularCauchyTailBudgetUp$ sibling chapters. The route still exposes only the
finite window, membership, unary-history, budget, tail-budget, readback, and
seal rows.

Finally apply
\autoref{thm:streamname-finite-window-regularity-real-seal-nonescape}. Its
finite-window Real seal boundary is exactly the row list displayed above, so
the sibling handoff cannot export quotient stream equality, selected limits,
countable-choice selectors, host real equality, metric completeness, or ambient
$\RealUp$ completeness.
\end{proof}

\begin{theorem}[StreamName budget tail regular seal lock]
\label{thm:streamname-budget-tail-regular-seal-lock}
Any finite $\StreamNameUp$ window routed through
$\ObservationBudgetLimiterUp$ and $\RegularCauchyTailBudgetUp$ reaches
$\RegSeqRatUp$ regularity and $\RealUp$ finite-seal data only through the
shared budget cap, tail threshold, finite window, dyadic ledger, readback, and
seal rows. The locked route exports no quotient streams, selected limits,
countable-choice selectors, host real equality, metric completeness, or
ambient completeness row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-real-regseq-finite-window-budget-handoff}.
It places every regularity row, dyadic tolerance row, and finite Real seal read
behind the shared observation-budget surface.

Next apply \autoref{thm:streamname-budget-handoff-sibling-chapter-route} and
\autoref{thm:streamname-regular-seal-sibling-route}. These force the limiter
cap, tail threshold, finite StreamName window, dyadic ledger, RegSeqRat
readback, and Real seal rows to remain a single sibling route.

Finally use
\autoref{thm:observation-budget-limiter-cauchy-tail-budget-factorization},
\autoref{thm:regular-cauchy-tail-budget-observation-gate}, and
\autoref{thm:streamname-finite-window-regularity-real-seal-nonescape}. Their
combined non-escape clauses exclude quotient streams, selected limits,
countable-choice selectors, host real equality, metric completeness, and
ambient completeness from the locked tail-budget seal read.
\end{proof}

\begin{theorem}[StreamName budget CauchyLimitSeal pullback]
\label{thm:streamname-budget-cauchy-limit-seal-pullback}
Let an accepted finite $\StreamNameUp$ window be routed through
$\ObservationBudgetLimiterUp$ and $\RegularCauchyTailBudgetUp$, and let a
public $\RealUp$ or completion-facing $\CauchyLimitSealUp$ consumer read that
route. Then the consumed route factors through the same finite rows:
$$
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory},\quad \ObservationBudgetLimiterUp,\quad
\RegularCauchyTailBudgetUp,\quad \DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad \RealUp,
$$
together with the displayed $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ provenance. The pullback exposes exactly the budget cap, tail
threshold, finite StreamName window, dyadic ledger, RegSeqRat readback, and
Real seal already locked by the StreamName budget route. It exports no quotient
streams, selected host limits, countable-choice selectors, host real equality,
metric completeness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the finite-window budget handoff of
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff}. It places
the accepted StreamName window, $\mathsf{ProbeBundle}$ ledger,
$\mathsf{InBundle}$ membership rows, and $\mathsf{UnaryHistory}$ observations
before any regularity row, dyadic tolerance row, or $\RealUp$ seal row is
consumed.

Next attach the sibling route of
\autoref{thm:streamname-budget-handoff-sibling-chapter-route}. The route passes
through the $\ObservationBudgetLimiterUp$ budget cap and then through the
$\RegularCauchyTailBudgetUp$ tail service before the dyadic ledger,
$\RegSeqRatUp$ readback, and $\RealUp$ seal are exposed.

Now use the tail regular seal lock of
\autoref{thm:streamname-budget-tail-regular-seal-lock}. It identifies the
budget cap, tail threshold, finite window, dyadic ledger, readback, seal rows,
and visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
provenance as one locked finite route.

Finally pass the locked route through the $\CauchyLimitSealUp$ consumer
boundary. The public route boundary of
\autoref{thm:cauchy-limit-seal-public-route-boundary} confines every public
$\RealUp$ or completion-facing read to the displayed route packet, and the
downstream completion handoff of
\autoref{thm:cauchy-limit-seal-downstream-completion-handoff} lets a completion
consumer pull back only along that same scheduled window, dyadic observation
ledger, regular source row, completion row, and seal row. The non-escape
clauses from the cited StreamName and CauchyLimitSeal boundaries rule out
quotient streams, selected host limits, countable-choice selectors, host real
equality, metric completeness, and ambient $\RealUp$ completeness.
\end{proof}

\begin{theorem}[StreamName budget regular readback exhaustion]
\label{thm:streamname-budget-regular-readback-exhaustion}
Every accepted finite $\StreamNameUp$ window routed through
$\ObservationBudgetLimiterUp$ and $\RegularCauchyTailBudgetUp$ to a public
$\RealUp$ consumer or a completion-facing $\CauchyLimitSealUp$ consumer is
exhausted by the same finite readback route:
$$
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory},\quad \ObservationBudgetLimiterUp,\quad
\RegularCauchyTailBudgetUp,\quad \DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad \RealUp.
$$
The exhausted packet carries exactly the displayed $\mathsf{BHist}$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ provenance of the StreamName budget handoff.
It exports no quotient stream, selected host limit, countable-choice selector,
host real equality, metric completeness, or ambient completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-budget-cauchy-limit-seal-pullback}. It already
pulls every public $\RealUp$ read and every completion-facing
$\CauchyLimitSealUp$ read back to the finite StreamName budget route through
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, the
budget limiter, the regular tail budget, the dyadic core, the regular sequence
row, and the Real seal.

Next use \autoref{thm:streamname-budget-tail-regular-seal-lock}. The lock
identifies the shared budget cap, tail threshold, finite window, dyadic ledger,
readback, and seal rows as a single route with its visible $\mathsf{BHist}$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Finally apply
\autoref{thm:streamname-finite-window-regularity-real-seal-nonescape}. Its
non-escape clause excludes quotient streams, selected host limits,
countable-choice selectors, host real equality, metric completeness, and
ambient completeness from any such consumer read. Since the pullback and the
lock name the same carrier coordinates, the consumer has no remaining route
outside the displayed finite packet.
\end{proof}

\begin{theorem}[StreamName ObserverFilter finite-window handoff]
\label{thm:streamname-observer-filter-finite-window-handoff}
Every accepted finite $\ObserverFilterUp$ selected-subhistory handoff to
$\StreamNameUp$ enters the finite-window budget surface only through the
selected row $S$, observer ledger $L$, componentwise transports $R$, continuation
routes $C$, provenance $P$, and local name $N$. The omitted rows $O$ remain
boundary witnesses in the observer-filter ledger. They do not supply RegSeqRat
regularity, Real seal data, quotient stream equality, selected host limits,
countable-choice selectors, or host real equality to the StreamName consumer.
\end{theorem}
\begin{proof}
Start with the ObserverFilter handoff theorem
\autoref{thm:observer-filter-streamname-handoff}. It identifies the
stream-facing route of an accepted filter packet as the selected subhistory
through $S,L,R,C,P,N$.

Apply \autoref{thm:observer-filter-ledger-exactness}. The finite source ledger
is exhausted by the selected side and the omitted side, and the omitted side is
kept as $O$ rather than exported as StreamName data.

Now use \autoref{thm:streamname-real-regseq-finite-window-budget-handoff}. Once
the selected subhistory is read as a finite $\StreamNameUp$ window, every
regularity, dyadic tolerance, and $\RealUp$ seal row must pass through the
finite observation-budget surface.

Finally apply \autoref{thm:streamname-regular-seal-sibling-route}. The sibling
route carries no coordinates for quotient stream equality, selected host limits,
countable-choice selectors, host real equality, metric completeness, or ambient
$\RealUp$ completeness. Since $O$ is not part of the selected StreamName source,
omitted rows remain boundary ledger witnesses and cannot serve any of those
downstream roles.
\end{proof}
