\section{StreamName finite-window transport obligations}
\label{sec:streamname-finite-window-transport-obligations}

\begin{theorem}[StreamName finite-window pointwise transport]
\label{thm:streamname-window-pointwise-transport}
Let $s,t,s',t':\mathsf{BHist}\to\mathsf{BHist}$ be certified
$\StreamNameUp$ rows, let $\mathcal{P}:\mathsf{ProbeBundle}$ be a finite
observation bundle, and suppose
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})
$$
is displayed together with the finite ledger rows
$\mathsf{UnaryHistory}(n)$ and $\mathsf{InBundle}(n,\mathcal{P})$ for every
selected observation. Suppose also that every selected $n$ carries the
pointwise transport rows
$$
\hsame(s(n),s'(n))
\qquad\text{and}\qquad
\hsame(t(n),t'(n)),
$$
and that the consumer route reads the source window only through displayed
$\Cont$ rows. Then the transported window exported to any $\RegSeqRat$ or
finite-window $\RealUp$ consumer is exactly
$$
\mathsf{RatStreamNameFiniteWindowClassifier}(s',t',\mathcal{P})
$$
with the same $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$,
$\mathsf{UnaryHistory}$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$
rows.

No infinite stream object, quotient stream equality, selected real value,
host Nat stream, or $\RealUp$ completeness principle is exported by this
transport.
\end{theorem}
\begin{proof}
First read the source finite window through the public handoff surface of
\autoref{thm:streamname-real-regseq-finite-window-handoff}. The available
rows are the selected rational-history classifier rows, the finite
$\mathsf{ProbeBundle}$ ledger, membership rows, unary observation rows, and
their local naming data.

Next apply the pointwise handoff and transport rows of
\autoref{thm:streamname-regseqrat-pointwise-handoff} and
\autoref{thm:streamname-regseqrat-observation-stability}. These identify the
transported classifier by using only the displayed pointwise $\hsame$ rows at
the certified observations of $\mathcal{P}$.

Finally replay the result through the finite pullback criterion of
\autoref{thm:streamname-regseqrat-realup-finite-window-pullback-criterion}.
The criterion records the same $\Cont$, $\Pkg$, and local certificate rows as
consumer-visible coordinates, so the transported packet remains the finite
window over $\mathcal{P}$ and exports none of the excluded stream, quotient,
real-value, host-index, or completeness data.
\end{proof}

\begin{theorem}[StreamName constant-window classifier stability]
\label{thm:streamname-constant-window-classifier-stability}
Let $d,e:\mathsf{BHist}$ be rational-history endpoints and let
$r,q:\mathsf{BHist}\to\mathsf{BHist}$ be certified observation schedules over
a finite bundle $\mathcal{P}:\mathsf{ProbeBundle}$. Suppose the constant
window displays the rational point classifier for $d$ and $e$, the selected
bundle rows $\mathsf{InBundle}(n,\mathcal{P})$, the unary ledger rows
$\mathsf{UnaryHistory}(n)$, pointwise $\hsame$ transport for the scheduled
constant observations, displayed $\Cont$ routes, $\Pkg$ provenance, and the
local $\NameCert_{\StreamNameUp}$ row. Then every transported constant
certified window preserves the same point classifier and ledger rows for the
$\RegSeqRat$ and finite-window $\RealUp$ handoff.

The stable constant-window packet contains no infinite stream object,
quotient stream equality, selected real value, host Nat stream, or
$\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Begin with the constant boundary of
\autoref{thm:streamname-real-regseq-constant-boundary}. It says that the
constant window contributes only the rational point classifier, finite bundle
ledger, membership rows, unary observation rows, and local naming data.

Transport the scheduled constant observations by
\autoref{thm:streamname-realup-constant-observation-handoff}. The handoff
reads the same endpoint classifier pointwise and leaves regularity, dyadic
seal data, and the $\RealUp$ seal classifier on the consumer side.

Now use \autoref{thm:streamname-regseqrat-pointwise-handoff} to identify the
consumer-facing packet. The pointwise rows, bundle membership, unary ledger,
displayed $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local
certificate row are precisely the rows named by the theorem statement, so the
constant classifier and ledger are stable under the certified transport.
\end{proof}

\begin{theorem}[StreamName RegSeqRat window handoff exactness]
\label{thm:streamname-regseq-window-handoff-exactness}
Let $\mathcal{W}$ be a finite $\StreamNameUp$ window over
$s,t:\mathsf{BHist}\to\mathsf{BHist}$ with selected bundle
$\mathcal{P}:\mathsf{ProbeBundle}$. The exact $\RegSeqRat$ handoff surface
read from $\mathcal{W}$ consists only of the finite window classifier
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})$, the
selected point certificates $\mathsf{RatHistoryClassifier}(s(n),t(n))$, the
pointwise $\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ ledger rows, the
displayed $\hsame$ transports, the $\Cont$ route rows, the $\Pkg$ provenance
row, and the local $\NameCert_{\StreamNameUp}$ row.

Conversely, those finite rows determine the whole source packet handed to
$\RegSeqRat$; no other StreamName coordinate is read. In particular, the
handoff exports no infinite stream object, quotient stream equality, selected
real value, host Nat stream, $\RegSeqRat$ regularity witness supplied by
StreamName, or $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
For the forward direction, project $\mathcal{W}$ through
\autoref{thm:streamname-real-regseq-finite-window-handoff}. It exposes the
finite StreamName window rows, selected rational-history classifier rows,
probe-bundle ledger, bundle membership, and unary-history observations.

Apply the pointwise handoff theorem
\autoref{thm:streamname-regseqrat-pointwise-handoff}. It refines the same
source packet to point certificates
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ at exactly the selected certified
observations of $\mathcal{P}$.

For the reverse direction, repack the displayed classifier, point
certificates, ledger rows, $\hsame$ transports, route rows, package
provenance, and local certificate row through
\autoref{thm:streamname-regseqrat-realup-finite-window-pullback-criterion}.
The criterion says that these are precisely the finite pullback coordinates
seen by the downstream consumers, so the source handoff is fully determined.

Finally use \autoref{thm:streamname-real-regseq-obligation-separation}. It
keeps $\RegSeqRat$ regularity and $\RealUp$ seal or completeness obligations
outside the StreamName source packet, and it rules out the infinite-stream,
quotient, selected-real, and host-index data excluded above.
\end{proof}

\begin{theorem}[StreamName finite-window transport RegSeqRat Real readiness]
\label{thm:streamname-finite-window-transport-regseqrat-real-readiness}
A transported finite $\StreamNameUp$ window is ready for $\RegSeqRat$ and finite-window $\RealUp$ consumers exactly when the finite-window classifier, selected point certificates, $\mathsf{UnaryHistory}$ rows, $\mathsf{InBundle}$ rows, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\StreamNameUp}$ row are all present in the source packet. This readiness surface exports no quotient stream equality, host Nat stream, selected real value, $\RegSeqRat$ regularity row, or $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
First apply pointwise transport, \autoref{thm:streamname-window-pointwise-transport}. It moves the finite classifier to the transported window while preserving the same bundle, membership, unary-history, pointwise $\hsame$, route, provenance, and local naming rows.

Use constant-window classifier stability when the selected observations are constant endpoints. Theorem~\ref{thm:streamname-constant-window-classifier-stability} shows that the same finite classifier and ledger rows remain the consumer-facing surface for $\RegSeqRat$ and finite-window $\RealUp$ handoff.

Next apply RegSeqRat window handoff exactness, \autoref{thm:streamname-regseq-window-handoff-exactness}. It identifies the complete source packet as the finite-window classifier, selected point certificates, $\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ data.

Finally cite the pointwise handoff theorem \autoref{thm:streamname-regseqrat-pointwise-handoff}. It keeps $\RegSeqRat$ regularity and $\RealUp$ completion obligations on the downstream side, so the transported StreamName source packet is ready for those consumers without exporting quotient stream equality, a host Nat stream, a selected real value, regularity, or completeness.
\end{proof}

\begin{theorem}[StreamName finite-window section transport closure]
\label{thm:streamname-finite-window-section-transport-closure}
Let $\mathcal{S}$ be an accepted finite $\StreamNameUp$ window section whose displayed rows contain the finite classifier, selected point certificates, $\mathsf{UnaryHistory}$ observations, $\mathsf{InBundle}$ ledger, componentwise $\BHist$ rows, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\StreamNameUp}$ registration. If $\mathcal{S}$ is transported through those displayed $\hsame$ and $\Cont$ rows, then the downstream $\RegSeqRatUp$ readback, the $\DyadicRatCoreUp$ tolerance ledger, and the finite-window $\RealUp$ seal remain on that same transported section route.

Conversely, any current Phase Real and Completion read that exposes the same finite $\StreamNameUp$ window, dyadic ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, and displayed $\BHist,\hsame,\Cont,\Pkg,\NameCert$ rows is read as the transported section $\mathcal{S}$. This section closure exports no quotient stream, selected limit, host sequence equality, ambient $\RealUp$ completeness, metric completeness, or standard bridge row.
\end{theorem}
\begin{proof}
For the forward direction, apply the pointwise transport theorem \autoref{thm:streamname-window-pointwise-transport}. It moves the accepted finite window through the displayed $\hsame$ rows while preserving the same bundle, membership, unary-history, continuation, provenance, and local naming surface.

Next apply RegSeqRat window handoff exactness, \autoref{thm:streamname-regseq-window-handoff-exactness}. The handoff identifies the downstream readback with exactly the transported finite-window classifier and selected point certificates, so the $\RegSeqRatUp$ read remains on the same section route.

Finally use the readiness theorem \autoref{thm:streamname-finite-window-transport-regseqrat-real-readiness}. It states that the finite classifier, point certificates, dyadic tolerance ledger, transports, routes, provenance, and local naming are sufficient for the finite-window $\RealUp$ consumer, while regularity and completion obligations stay downstream.

For the converse direction, inspect the exposed Phase Real and Completion read. If it shows the same finite StreamName window, dyadic ledger, RegSeqRat readback, Real seal, and displayed $\BHist,\hsame,\Cont,\Pkg,\NameCert$ rows, then the preceding exactness and readiness results reconstruct the unique transported section route read by those consumers. The exclusions follow because none of the cited rows contains quotient streams, selected limits, host sequence equality, ambient Real completeness, metric completeness, or standard bridge data.
\end{proof}

\begin{theorem}[StreamName pointwise transport scope]
\label{thm:streamname-pointwise-transport-scope}
Let $\mathcal{S}$ be an accepted transported finite $\StreamNameUp$ packet
over a finite bundle $\mathcal{P}:\mathsf{ProbeBundle}$, with source and
target schedules $s,t,s',t':\mathsf{BHist}\to\mathsf{BHist}$. Before any
$\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ consumer reads
$\mathcal{S}$, the packet exposes exactly the following StreamName-side
rows: the finite classifier
$\mathsf{RatStreamNameFiniteWindowClassifier}(s',t',\mathcal{P})$, the
selected point-certificate rows
$\mathsf{RatHistoryClassifier}(s'(n),t'(n))$ at the displayed observations,
the support rows $\mathsf{UnaryHistory}(n)$ and
$\mathsf{InBundle}(n,\mathcal{P})$, the componentwise $\hsame$ transports
from $s(n),t(n)$ to $s'(n),t'(n)$, the replayed $\Cont$ routes, the $\Pkg$
provenance, and the local $\NameCert_{\StreamNameUp}$ row.

The same scope exports no quotient stream equality, host sequence equality,
selected limit, $\RealUp$ completeness principle, metric-completeness datum,
countable-choice row, or standard bridge row. Thus the finite-window packet
seen by $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ consumers is a
finite transported row packet, not a hidden stream quotient or completion
claim.
\end{theorem}
\begin{proof}
Start with pointwise transport,
\autoref{thm:streamname-window-pointwise-transport}. It transports the
finite classifier across the displayed $\hsame$ rows and preserves the same
bundle, support, continuation, provenance, and local naming surface.

Next use the handoff exactness theorem
\autoref{thm:streamname-regseq-window-handoff-exactness}. This identifies
the rows read by $\RegSeqRatUp$ as the finite classifier, selected point
certificates, support rows, transports, routes, provenance, and local
certificate, and it rules out any additional StreamName coordinate.

Then apply readiness,
\autoref{thm:streamname-finite-window-transport-regseqrat-real-readiness}.
Readiness says that the same rows are sufficient for the finite-window
$\RealUp$ route while quotient equality, host sequence data, selected real
values, regularity, and completeness obligations remain outside the source
packet.

Finally compose with section transport closure,
\autoref{thm:streamname-finite-window-section-transport-closure}. The
closure theorem keeps the $\RegSeqRatUp$ readback, the
$\DyadicRatCoreUp$ tolerance ledger, and the finite-window $\RealUp$ seal on
the same transported section route. Its exclusion list supplies the stated
absence of selected limits, metric completeness, and standard bridge rows,
so the displayed row list is exactly the scope available before the
downstream consumers read the packet.
\end{proof}
