\section{StreamName finite-request section pullback}
\label{sec:streamname-finite-request-section-pullback}

\begin{theorem}[StreamName finite-request section pullback]
\label{thm:streamname-finite-request-section-pullback}
Every finite request section that faces $\RealUp$ through the
$\RegSeqRatUp$-to-$\RealUp$ seal pulls back to the same displayed
$\StreamNameUp$ section schedule, the same $\DyadicRatCoreUp$ endpoint and
radius ledger, the same $\RegSeqRatUp$ regularity and readback surface, the
same componentwise $\hsame$ rows, the same displayed $\Cont$ routes, the same
$\Pkg$ provenance, and the same local $\NameCert$ rows. Thus a RealUp-facing
request has no route around the displayed $\StreamNameUp$,
$\DyadicRatCoreUp$, and $\RegSeqRatUp$ rows.
\end{theorem}
\begin{proof}
Start with the finite endpoint section of
\autoref{thm:streamname-real-endpoint-finite-request-section}. It reads the
RealUp-facing request as a finite $\StreamNameUp$ section whose visible
coordinates are the endpoint, certified observation, support, and local naming
rows.

Next apply \autoref{thm:streamname-regseqrat-window-budget-section}. The
$\RegSeqRatUp$ readback and $\DyadicRatCoreUp$ budget rows consumed by the same
request are not independent rows; they are the window-budget face of the same
finite section.

Now use
\autoref{thm:streamname-finite-request-section-real-seal-lock} and
\autoref{thm:streamname-finite-request-real-seal-totality}. The
$\RegSeqRatUp$-to-$\RealUp$ seal is exhausted by the displayed StreamName
schedule, DyadicRatCore endpoint-radius ledger, RegSeqRat regularity/readback
surface, and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$.

Finally compare with the Real-side route. Apply
\autoref{thm:real-regseqrat-finite-request-fusion} to repack the RealUp-facing
request as the same finite packet, and apply
\autoref{thm:real-regseqrat-terminal-budget-exhaustion} to rule out a second
terminal-budget face. The pullback is therefore the displayed StreamName,
DyadicRatCore, RegSeqRat, and support-row section already named above.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real finite-request section lock]
\label{thm:streamname-regseqrat-real-finite-request-section-lock}
Let $\mathcal{R}$ and $\mathcal{S}$ be two presentations of a
$\RegSeqRatUp$-to-$\RealUp$ seal over the same finite request. The
presentations agree exactly when their displayed section rows agree: the
$\StreamNameUp$ schedule, the $\DyadicRatCoreUp$ endpoint and radius ledger,
the $\RegSeqRatUp$ regularity and readback surface, componentwise $\hsame$,
displayed $\Cont$, $\Pkg$ provenance, and local $\NameCert$ rows. No further
RealUp-facing coordinate can distinguish the two presentations.
\end{theorem}
\begin{proof}
For the forward direction, read both presentations through
\autoref{thm:streamname-finite-request-section-pullback}. Since the finite
request is the same, the pullback exposes the same StreamName schedule,
DyadicRatCore ledger, RegSeqRat surface, and BEDC support rows for both
presentations.

For the reverse direction, suppose the displayed section rows agree. Apply
\autoref{thm:streamname-open-phase-request-handoff} to each presentation. Both
seal presentations are then the same local handoff through $\StreamNameUp$,
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$.

It remains to see that the Real-facing seal cannot add a separating row. Use
\autoref{thm:streamname-finite-request-section-real-seal-lock} to place each
presentation behind the same finite section, and use
\autoref{thm:streamname-finite-request-real-seal-totality} together with
\autoref{thm:real-regseqrat-terminal-budget-exhaustion} to exhaust the terminal
seal surface by those rows. Hence agreement of the displayed section rows is
both necessary and sufficient.
\end{proof}

\begin{theorem}[StreamName finite-request section classifier pullback]
\label{thm:streamname-finite-request-section-classifier-pullback}
Let $Q$ and $Q'$ be RealUp-facing finite requests on the terminal L10
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ route. Suppose that the
two requests display the same $\StreamNameUp$ section schedule, the same
$\DyadicRatCoreUp$ endpoint-radius ledger, the same $\RegSeqRatUp$
regularity and readback surface, the same $\RealUp$ seal boundary, and the
same support rows $\BHist$, componentwise $\hsame$, displayed $\Cont$ routes,
$\Pkg$ provenance, and local $\NameCert$ rows. Then $Q$ and $Q'$ pull back to
the same finite carrier verdict and the same classifier verdict on that
terminal four-face route.

The pullback uses only the displayed four faces and the named support rows. It
exports no quotient stream equality, no host sequence equality, no selected
limit, no ambient completeness row, no countable-choice row, and no bridge
row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-request-section-pullback} to both
$Q$ and $Q'$. The two RealUp-facing requests are read through the displayed
StreamName schedule, DyadicRatCore endpoint-radius ledger, RegSeqRat
regularity/readback surface, RealUp seal boundary, and support rows named in
the hypotheses.

Next use \autoref{thm:streamname-regseqrat-real-finite-request-section-lock}.
Since those displayed rows agree, the two seal presentations have the same
finite request section at the terminal route.

Now apply \autoref{thm:streamname-finite-section-classifier-determinacy}. The
common finite section fixes the carrier verdict and classifier verdict read by
the $\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ four-face route, so
there is no second classifier route for either request.

Finally apply \autoref{thm:streamname-finite-request-section-nonescape}. The
common verdict is supported only by the displayed faces and support rows, and
the excluded quotient stream equality, host sequence equality, selected limit,
ambient completeness, countable-choice, and bridge rows are not part of the
pullback.
\end{proof}

\begin{theorem}[StreamName finite-request section pullback exactness]
\label{thm:streamname-finite-request-section-pullback-exactness}
Let $Q$ and $Q'$ be RealUp-facing finite requests on the terminal L10
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ route. The two requests
determine the same finite carrier verdict and the same classifier verdict if
and only if their displayed four-face pullbacks agree on the $\StreamNameUp$
section schedule, the $\DyadicRatCoreUp$ endpoint-radius ledger, the
$\RegSeqRatUp$ regularity and readback surface, the $\RealUp$ seal boundary,
and the support rows $\BHist$, componentwise $\hsame$, displayed $\Cont$
routes, $\Pkg$ provenance, and local $\NameCert$ rows.

This equivalence is internal to the finite terminal packet. It excludes
quotient streams, host sequence equality, selected limits, ambient
completeness, countable choice, metric-completeness rows, and bridge rows.
\end{theorem}
\begin{proof}
For the forward direction, assume that $Q$ and $Q'$ determine the same finite
carrier verdict and classifier verdict. Apply
\autoref{thm:streamname-finite-request-section-classifier-pullback} to read
each verdict through the displayed terminal four-face route, and apply
\autoref{thm:streamname-regseqrat-real-finite-request-section-lock} to lock
the two seal presentations to the same finite request section.

The lock identifies exactly the StreamName schedule, DyadicRatCore
endpoint-radius ledger, RegSeqRat regularity/readback surface, RealUp seal
boundary, and support rows named in the statement. Hence the displayed
four-face pullbacks agree on every coordinate available to the finite verdict.

For the reverse direction, assume that the displayed four-face pullbacks agree
on those rows. Use \autoref{thm:streamname-finite-request-section-pullback} to
identify both requests with the same finite section on the terminal L10 route.
The classifier pullback theorem then reads that common section as the same
finite carrier verdict and the same classifier verdict.

Finally use \autoref{thm:streamname-finite-request-section-nonescape}. It
rules out off-route separating coordinates: no quotient stream, host sequence
equality, selected limit, ambient completeness, countable-choice row,
metric-completeness row, or bridge row can distinguish the two requests once
the displayed finite packet agrees.
\end{proof}

\begin{theorem}[StreamName finite-request section cofinal verdict invariance]
\label{thm:streamname-finite-request-section-cofinal-verdict-invariance}
Let $Q$ and $Q'$ be RealUp-facing finite requests on the terminal L10 route
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$. Suppose that $Q'$ is
obtained from $Q$ by an accepted cofinal refinement preserving the displayed
$\StreamNameUp$ section schedule, the $\DyadicRatCoreUp$ endpoint-radius
ledger, the $\RegSeqRatUp$ regularity and readback surface, the $\RealUp$ seal
boundary, and the support rows $\BHist$, componentwise $\hsame$, displayed
$\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows. Then $Q$ and
$Q'$ determine the same finite carrier verdict and the same classifier verdict
on the terminal four-face route.

This invariance is only a finite-request statement. It exports no quotient
stream equality, no host sequence equality, no selected limit, no ambient
completeness row, no countable-choice row, no metric-completeness row, and no
bridge row.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-finite-request-section-pullback-exactness}. It is
enough to identify the displayed four-face pullbacks for $Q$ and $Q'$: the
StreamName schedule, DyadicRatCore endpoint-radius ledger, RegSeqRat
regularity and readback surface, RealUp seal boundary, and named BEDC support
rows.

The accepted cofinal refinement preserves the displayed StreamName section.
Use \autoref{thm:streamname-finite-section-restriction-exactness} to read this
preservation as equality of the finite section restrictions seen by the
terminal request.

For the RegSeqRat-to-Real part, apply
\autoref{thm:regseqrat-finite-request-section-refinement-composition}. The
compatible refinement composition transports the RegSeqRat regularity/readback
surface together with the RealUp-facing seal boundary, so the refined request
has the same terminal four-face display.

Now use
\autoref{thm:streamname-regseqrat-real-finite-request-section-lock}. The lock
prevents the seal presentation from adding a distinguishing coordinate once
the displayed StreamName, DyadicRatCore, RegSeqRat, RealUp, and support rows
agree.

Finally apply \autoref{thm:streamname-finite-request-section-nonescape}. The
excluded quotient stream equality, host sequence equality, selected limit,
ambient completeness, countable-choice, metric-completeness, and bridge rows
therefore cannot separate the finite carrier verdict or the classifier verdict.
\end{proof}

\begin{theorem}[StreamName finite-request section nonescape]
\label{thm:streamname-finite-request-section-nonescape}
The finite-request section pullback of
\autoref{thm:streamname-finite-request-section-pullback} exports no quotient
stream equality, no host sequence equality, no selected limit, no host real
equality, no countable-choice row, no ambient completion, no
metric-completeness row, and no $\RealUp$ completeness datum. Its public
surface is only the displayed $\StreamNameUp$ schedule, $\DyadicRatCoreUp$
endpoint-radius ledger, $\RegSeqRatUp$ regularity/readback surface, and the
support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-request-section-pullback}. The
RealUp-facing request has already been pulled back to the displayed
StreamName, DyadicRatCore, RegSeqRat, and support-row section.

Next apply \autoref{thm:streamname-finite-request-section-real-seal-lock}. The
seal lock blocks quotient stream equality, host real equality, ambient
completion points, and RealUp completeness data from the seal presentation.

Now use \autoref{thm:streamname-finite-request-real-seal-totality} and
\autoref{thm:streamname-open-phase-request-handoff}. These results exhaust the
open-phase handoff by the four displayed faces and the support rows, leaving no
coordinate for host sequence equality, selected limits, countable choice, or a
metric-completeness row.

Finally apply the Real-side finite-request route
\autoref{thm:real-regseqrat-finite-request-fusion} and the terminal-budget
exhaustion of \autoref{thm:real-regseqrat-terminal-budget-exhaustion}. They
confirm that any RealUp-facing consumer reads the same finite packet rather
than an ambient completion or completeness datum.
\end{proof}
