\section{StreamName finite-section reindex gluing}
\label{sec:streamname-finite-section-reindex-gluing}

\begin{theorem}[StreamName finite-section reindex gluing]
\label{thm:streamname-finite-section-reindex-gluing}
Let $Q$ and $Q'$ be accepted current Phase Real and Completion finite request
sections of a $\StreamNameUp$ packet. Suppose that a certified
$\StreamNameUp$ finite-window reindex route transports the finite window of
$Q$ to the finite window of $Q'$, and suppose that after this transport the two
sections agree on the $\DyadicRatCoreUp$ endpoint-radius ledger, the
$\RegSeqRatUp$ readback and regularity rows, the $\RealUp$ seal boundary, and
the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support
rows. Then $Q$ and $Q'$ determine the same terminal four-face route
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ and the same public
carrier and classifier verdict at that route.

The glued route remains finite and displayed. It contains no quotient stream,
selected limit, host equality, countable-choice row, metric-completeness row,
ambient $\RealUp$ completeness row, aggregate status row, or standard bridge
row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-window-reindex-determinacy}. The certified
finite-window reindex route, together with the transported $\BHist$, $\Cont$,
$\Pkg$, and $\NameCert$ rows and the $\hsame$ compatibility, identifies the two
finite observation sections after transport.

Next use \autoref{thm:streamname-reindex-terminal-coverage}. The transported
finite observation section reaches exactly the four terminal faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, with the same
DyadicRatCore ledger, RegSeqRat readback, RealUp seal boundary, and displayed
support rows.

Now apply \autoref{thm:streamname-finite-section-pullback-exactness} to $Q$
and to $Q'$. Pullback exactness reads both accepted request sections through
the same four-face finite route once the endpoint-radius ledger, regularity
rows, readback rows, seal boundary, and displayed support rows have been
transported to agreement.

Finally apply
\autoref{thm:streamname-finite-section-classifier-determinacy}. The common
four-face route leaves no second public carrier surface or classifier surface
on which the verdict could vary. The exclusion clauses follow from the same
finite support: the construction never exports a quotient stream, selected
limit, host equality, countable-choice row, metric-completeness row, ambient
Real completeness row, aggregate status row, or standard bridge row.
\end{proof}

\begin{theorem}[StreamName finite-section reindex cocycle]
\label{thm:streamname-finite-section-reindex-cocycle}
Let $Q_0$, $Q_1$, and $Q_2$ be accepted current Phase Real and Completion
finite request sections of a $\StreamNameUp$ packet. Suppose that certified
$\StreamNameUp$ finite-window reindex routes transport the finite window of
$Q_0$ to the finite window of $Q_1$ and the finite window of $Q_1$ to the
finite window of $Q_2$. Suppose also that the two transported sections agree
on the same $\DyadicRatCoreUp$ endpoint-radius ledger, the $\RegSeqRatUp$
readback and regularity rows, the $\RealUp$ seal boundary, and the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Then the
direct composite route from $Q_0$ to $Q_2$ determines the same terminal
four-face route $\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ and the
same public carrier and classifier verdict as the two-step route through
$Q_1$.

The cocycle comparison remains finite and displayed. It contains no quotient
stream, selected limit, host equality, countable-choice row,
metric-completeness row, ambient $\RealUp$ completeness row, aggregate status
row, or standard bridge row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-section-reindex-gluing} to the
overlap from $Q_0$ to $Q_1$ and again to the overlap from $Q_1$ to $Q_2$. The
shared endpoint-radius ledger, readback rows, regularity rows, seal boundary,
and displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows give
the two adjacent finite gluing identifications.

Next use \autoref{thm:streamname-public-reindexing-associative-law}. The
certified two-step finite-window route and the direct composite route from
$Q_0$ to $Q_2$ present the same public reindexing data, so the intermediate
section $Q_1$ cannot contribute a second terminal presentation.

Now apply \autoref{thm:streamname-reindex-terminal-coverage}. Both the
two-step route and the direct composite route reach exactly the same four
terminal faces $\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, with no
extra face and with the same displayed support rows.

Finally apply
\autoref{thm:streamname-finite-section-classifier-determinacy}. Since the
terminal four-face route is common, the public carrier and classifier verdict
read from the composite route agrees with the verdict read from the two-step
route. The non-escape exclusions are inherited from the finite displayed
routes used in the two gluing steps: no quotient stream, selected limit, host
equality, countable choice, metric completeness, ambient Real completeness,
aggregate status row, or standard bridge row is introduced.
\end{proof}
