\section{StreamName finite-window lattice meet}
\label{sec:streamname-finite-window-lattice-meet}

\begin{definition}[StreamName finite-window lattice meet packet]
\label{def:streamname-finite-window-lattice-meet}
Let $\mathcal W_L$ and $\mathcal W_R$ be accepted finite-window
$\StreamNameUp$ packages over displayed source maps $s,t:\mathsf{BHist}\to
\mathsf{BHist}$. A StreamName finite-window lattice meet packet for
$(\mathcal W_L,\mathcal W_R)$ is the finite $\mathsf{BHist}$ surface
$$
\mathcal M=(Q,B,I,U,D,H,C,P,N_L,N_R)
$$
whose rows are as follows:
\begin{enumerate}
\item $Q$ is the common selected rational classifier row
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal Q)$ read on the
shared $\mathsf{ProbeBundle}$ $\mathcal Q$;
\item $B$ is the displayed $\mathsf{ProbeBundle}$ row for $\mathcal Q$,
together with its restrictions to the selected bundles of $\mathcal W_L$ and
$\mathcal W_R$;
\item $I$ is the family of $\mathsf{InBundle}(n,\mathcal Q)$ membership rows
for selected unary observations;
\item $U$ is the family of $\mathsf{UnaryHistory}(n)$ observation rows paired
with the pointwise rational classifier rows read by $Q$;
\item $D$ is the dyadic ledger surface handed to $\RegSeqRat$ and to the
finite-window $\RealUp$ consumer, including endpoint, radius, denominator,
and finite ledger-policy rows;
\item $H$ is the componentwise $\hsame$ transport comparing selected rational
classifier rows, probe rows, membership rows, unary rows, dyadic rows,
handoff rows, provenance rows, and local names;
\item $C$ is the displayed $\Cont$ route ledger from each accepted
$\StreamNameUp$ window through the meet surface to the $\RegSeqRat$ handoff
and the finite-window $\RealUp$ seal;
\item $P$ is the $\Pkg$ provenance over the accepted windows, the
synchronized-window union, the cover-refinement classifier, the common-window
transport, and the Real--RegSeq handoff boundary;
\item $N_L$ and $N_R$ are the local $\NameCert_{\StreamNameUp}$ rows proving
that the left and right accepted packages expose this same meet surface.
\end{enumerate}
The packet is only this finite observation surface. It has no coordinate for
quotient stream equality, host index equality, selected limits, host real
equality, or ambient completeness.

This meet packet is the $\StreamNameUp$-side sibling surface consumed by
\autoref{ch:concrete-instances-regseqrat-namecert} and
\autoref{ch:concrete-instances-real-namecert}, with its dyadic ledger row
routed through \autoref{ch:concrete-instances-dyadicratcore-namecert}.
\end{definition}

\begin{theorem}[StreamName finite-window lattice meet exhaustion]
\label{thm:streamname-finite-window-lattice-meet-exhaustion}
Let $\mathcal M$ be a StreamName finite-window lattice meet packet for two
accepted finite-window $\StreamNameUp$ packages. Every $\RegSeqRat$ consumer
or finite-window $\RealUp$ consumer of $\mathcal M$ reads only the common
selected rational classifier rows, the $\mathsf{ProbeBundle}$ rows, the
$\mathsf{InBundle}$ membership rows, the $\mathsf{UnaryHistory}$ observation
rows, the dyadic ledger rows, the componentwise transports, the continuation
routes, the package provenance, and the local naming rows displayed in
\autoref{def:streamname-finite-window-lattice-meet}.

Consequently the meet packet is a shared finite observation surface for the
RegSeqRat and RealUp handoffs. It does not provide quotient stream equality,
host index equality, selected limits, host real equality, ambient
completeness, or any consumer-visible row outside the finite StreamName,
RegSeqRat, and RealUp ledger surfaces listed above.
\end{theorem}
\begin{proof}
First pass both accepted windows through
\autoref{thm:streamname-public-finite-window-interface}. The public interface
restricts each window to its finite classifier, probe bundle, membership,
unary-history, pointwise rational classifier, $\hsame$, $\Cont$, $\Pkg$, and
local naming rows.

Next apply \autoref{thm:streamname-synchronized-window-union-carrier}. The
two accepted windows are repacked over one synchronized carrier, so their
shared selected observations have one displayed $\mathsf{ProbeBundle}$ row,
one membership family, one unary-history family, and one provenance ledger.

Use \autoref{thm:streamname-finite-window-cover-refinement-classifier} to
read the common probe bundle as a covered finite-window classifier. The
cover-refinement step supplies the common selected rational classifier row
and keeps the selected endpoint package on the same finite observation rows.

Now apply \autoref{thm:streamname-regseqrat-common-window-transport}. Any
$\RegSeqRat$ handoff through the left or right accepted window reads the same
common-window surface, with the same componentwise $\hsame$ transports,
continuation routes, and package provenance.

Finally use
\autoref{thm:streamname-regseqrat-realup-source-boundary-exhaustion} together
with \autoref{thm:streamname-real-regseq-obligation-separation}. These
handoff results identify the dyadic ledger rows and the finite-window RealUp
consumer rows, while keeping regularity, sealing, limits, quotient rows, host
index equality, host real equality, and ambient completeness outside the meet
packet. The displayed coordinates of $\mathcal M$ therefore exhaust every
consumer read.
\end{proof}

\begin{theorem}[StreamName finite-window lattice meet associativity]
\label{thm:streamname-finite-window-lattice-meet-associativity}
Let $\mathcal W_A,\mathcal W_B,\mathcal W_C$ be accepted finite-window
$\StreamNameUp$ packages over displayed source maps. Suppose that
$\mathcal M_{AB}$, $\mathcal M_{BC}$, $\mathcal M_{(AB)C}$, and
$\mathcal M_{A(BC)}$ are accepted StreamName finite-window lattice meet
packets whose common selected observations are read on the same finite
$\mathsf{ProbeBundle}$ after reassociating the three local
$\NameCert_{\StreamNameUp}$ rows. Then the two iterated meet packets
$\mathcal M_{(AB)C}$ and $\mathcal M_{A(BC)}$ expose the same common
observation surface.

More precisely, reassociation changes only the bracketing of the three local
$\NameCert_{\StreamNameUp}$ rows. The selected rational classifier rows,
$\mathsf{ProbeBundle}$ rows, $\mathsf{InBundle}$ membership rows,
$\mathsf{UnaryHistory}$ observation rows, dyadic ledger rows, componentwise
$\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the
RegSeqRat and finite-window RealUp handoff rows are unchanged. Neither
iterated meet exports quotient stream equality, host index equality, selected
limits, host real equality, ambient completeness, or any consumer-visible row
outside the finite StreamName, RegSeqRat, and RealUp ledger surfaces.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-finite-window-lattice-meet-exhaustion} to
$\mathcal M_{AB}$ and $\mathcal M_{BC}$. Each binary meet is exhausted by its
selected rational classifier, probe-bundle, membership, unary-history,
dyadic, transport, continuation, provenance, and local naming rows.

Apply the same exhaustion theorem to the two iterated packets
$\mathcal M_{(AB)C}$ and $\mathcal M_{A(BC)}$. By hypothesis these packets
read the same finite $\mathsf{ProbeBundle}$ after reassociating the local
NameCert rows, so the classifier, membership, unary-history, dyadic,
transport, continuation, provenance, RegSeqRat, and finite-window RealUp
handoff rows are the same displayed rows on both sides.

It remains to compare the local naming coordinates. Use
\autoref{lem:streamname-finite-window-lattice-meet-symmetry} to commute the
binary meet packets inside either bracketing until the three local
$\NameCert_{\StreamNameUp}$ rows are read in the chosen reassociated order.
Symmetry fixes $Q,B,I,U,D,H,C,P$ and exchanges only already displayed local
naming rows, so no downstream consumer receives a new row during the
reassociation.

The exhaustion theorem now applies once more to the reassociated iterated
surface. Since every RegSeqRat or finite-window RealUp consumer is confined
to the displayed finite rows, and those rows agree for
$\mathcal M_{(AB)C}$ and $\mathcal M_{A(BC)}$, the two iterated meets expose
the same common observation surface and no excluded quotient, host, limit,
real-equality, completeness, or hidden consumer coordinate.
\end{proof}

\begin{lemma}[StreamName finite-window lattice meet symmetry]
\label{lem:streamname-finite-window-lattice-meet-symmetry}
Let $\mathcal W_L$ and $\mathcal W_R$ be accepted finite-window
$\StreamNameUp$ packages over displayed source maps $s,t:\BHist\to
\BHist$. Suppose that
$$
\mathcal M=(Q,B,I,U,D,H,C,P,N_L,N_R)
$$
is an accepted StreamName finite-window lattice meet packet for
$(\mathcal W_L,\mathcal W_R)$. Then
$$
\mathcal M^{\mathrm{op}}=(Q,B,I,U,D,H,C,P,N_R,N_L)
$$
is an accepted StreamName finite-window lattice meet packet for
$(\mathcal W_R,\mathcal W_L)$ over the same common observation surface.
The rows $Q,B,I,U,D,H,C,P$ are unchanged, and the only exchanged
coordinates are the two local $\NameCert_{\StreamNameUp}$ rows.

Consequently every $\RegSeqRat$ consumer or finite-window $\RealUp$ consumer
of $\mathcal M^{\mathrm{op}}$ reads exactly the same selected rational
classifier row, probe-bundle row, membership rows, unary-history rows, dyadic
ledger row, componentwise transport row, continuation route row, and package
provenance row as it reads from $\mathcal M$, with the left and right local
naming rows interchanged. The symmetric packet exports no quotient stream
equality, host index equality, selected limit, host real equality, ambient
completeness, or consumer-visible row outside the finite meet surface.
\end{lemma}
\begin{proof}
Unpack the meet packet using
\autoref{def:streamname-finite-window-lattice-meet}. The coordinate $Q$ is
read on the shared $\mathsf{ProbeBundle}$, $B$ is the same displayed bundle
row together with its two restrictions, and $I,U,D,H,C,P$ are common rows over
that same finite surface. None of these rows carries an additional coordinate
that distinguishes the ordered pair $(\mathcal W_L,\mathcal W_R)$ from the
ordered pair $(\mathcal W_R,\mathcal W_L)$ after the same two restrictions
are read in the opposite order.

The only ordered coordinates in the displayed packet are the local naming
rows. In $\mathcal M$, the row $N_L$ proves that the left accepted package
$\mathcal W_L$ exposes the meet surface, and $N_R$ proves that the right
accepted package $\mathcal W_R$ exposes the same meet surface. For the ordered
pair $(\mathcal W_R,\mathcal W_L)$, the first local naming row must name
$\mathcal W_R$ and the second must name $\mathcal W_L$. These are precisely
$N_R$ and $N_L$. Thus the tuple
$(Q,B,I,U,D,H,C,P,N_R,N_L)$ satisfies the same packet clauses for the swapped
ordered pair.

It remains to identify what a downstream consumer can read. By
\autoref{thm:streamname-finite-window-lattice-meet-exhaustion}, every
$\RegSeqRat$ consumer and every finite-window $\RealUp$ consumer is confined
to the displayed classifier, bundle, membership, unary-history, dyadic,
transport, continuation, provenance, and local naming coordinates of the meet
packet. The construction of $\mathcal M^{\mathrm{op}}$ leaves the common
coordinates $Q,B,I,U,D,H,C,P$ fixed and merely exchanges the two already
displayed naming rows. Hence the swapped packet has the same consumer-facing
finite observation surface, with no route to any excluded quotient, host,
limit, real-equality, completeness, or hidden consumer row.
\end{proof}
