\section{StreamName Finite-Cover Support Removal Global Obstruction}
\label{sec:streamname-finite-cover-support-removal-global-obstruction}

This finite-cover support surface is the $\StreamNameUp$-side read of the
L10 route through
\autoref{ch:concrete-instances-dyadicratcore-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-real-namecert}: those sibling chapters supply
the dyadic ledger, regular-sequence readback, and terminal $\RealUp$ seal faces
consumed by the theorems in this file.

\begin{theorem}[StreamName finite-cover support removal global obstruction]
\label{thm:streamname-finite-cover-support-removal-global-obstruction}
Let $\{Q_i\}_{i \in I}$ be an accepted finite cover of current Phase
$\RealUp$ and Completion terminal $\StreamNameUp$ request sections feeding the
DyadicRatCore--RegSeqRat--Real four-face route. Suppose the accepted overlaps
display the same $\StreamNameUp$ finite-window row, the same
$\DyadicRatCoreUp$ ledger row, the same $\RegSeqRatUp$ readback row, the same
$\RealUp$ seal-visible source, and the same $\BHist$, componentwise $\hsame$,
$\Cont$, $\Pkg$, and local \NameCert{} support rows. If one displayed local
support row is deleted from any member $Q_j$, then the cover-descent terminal
support packet cannot present the same $\RealUp$ seal-visible source.

The obstruction is global over the finite cover: quotient stream equality,
selected limits, countable choice, metric-completeness data, aggregate
formalstatus rows, bridge rows, ambient $\RealUp$ completeness, or a replacement
regularity selector cannot supply the deleted row or restore the same
cover-descent source.
\end{theorem}
\begin{proof}
First restrict to the member where the deletion occurs. The local removal
witness theorem
\autoref{thm:streamname-terminal-support-removal-witness} says that deleting a
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or local \NameCert{} row from
the accepted terminal packet loses the carrier verdict, classifier verdict, or
consumer-facing terminal route of that local section.

Next descend through the finite cover. Apply
\autoref{thm:streamname-finite-cover-terminal-support-minimality}. The
cover-descent terminal packet is accepted exactly on the common
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces
together with the displayed support rows on the accepted overlaps. Therefore a
local deletion in $Q_j$ is not confined to a private presentation choice; it
removes one coordinate of the cover support itself.

Now localize the resulting cover defect. By
\autoref{thm:streamname-finite-cover-terminal-support-defect-localization}, a
failure of the cover-descent carrier verdict, classifier verdict, or terminal
route is witnessed on one accepted local section or accepted overlap, and the
witness lies on a displayed face or support row. In the present case the
witness is the deleted local support row, so the cover cannot still present the
same $\RealUp$ seal-visible source.

Finally rule out hidden replacement data. The selector nonchoice theorem
\autoref{thm:streamname-finite-window-regularity-selector-nonchoice} prevents
the $\RegSeqRatUp$ regularity row from re-entering as a hidden selector, host
function, countable-choice witness, quotient representative, selected limit,
ambient completeness coordinate, or independent completed-real carrier.
Together with the exclusion clauses in the finite-cover minimality and defect
localization theorems, this leaves no quotient equality, limit, choice,
metric-completeness datum, aggregate formalstatus row, bridge row, ambient
$\RealUp$ completeness principle, or replacement selector able to supply the
missing row.
\end{proof}

\begin{theorem}[StreamName finite-cover support invariance under refinement]
\label{thm:streamname-finite-cover-support-invariance-under-refinement}
Let $\{Q_i\}_{i \in I}$ and $\{R_k\}_{k \in K}$ be accepted finite covers of
the same current Phase $\RealUp$ and Completion terminal $\StreamNameUp$
request section. Suppose they admit an accepted common refinement
$\{S_\ell\}_{\ell \in L}$, and that after pullback to the refinement the two
covers agree on the four visible faces $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$, and on the displayed $\BHist$, componentwise
$\hsame$, $\Cont$, $\Pkg$, and local \NameCert{} rows. If one displayed local
support row is deleted in either original cover, then every accepted
refinement-equivalent presentation fails to present the same $\RealUp$
seal-visible source.

Equivalently, changing the finite-cover presentation cannot hide the missing
support row. Quotient stream equality, selected limits, countable choice,
metric-completeness data, aggregate formalstatus rows, bridge rows, ambient
$\RealUp$ completeness, and replacement regularity selectors are not
refinement coordinates for restoring that source.
\end{theorem}
\begin{proof}
Pull both finite covers to the accepted common refinement
$\{S_\ell\}_{\ell \in L}$. By hypothesis the pullbacks display the same
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces and
the same $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
\NameCert{} support rows. Thus the deleted row is a deleted coordinate of the
refined cover support, not merely a feature of one presentation.

Apply
\autoref{thm:streamname-finite-cover-terminal-support-minimality} to the
refined cover. The accepted terminal support packet on the refinement is
accepted exactly on the four visible faces and the displayed support rows.
Deleting one displayed local support row therefore removes a coordinate needed
for the same carrier verdict, classifier verdict, and terminal route.

Next localize the failure with
\autoref{thm:streamname-finite-cover-terminal-support-defect-localization}.
The defect is witnessed on one accepted refined local section or accepted
refined overlap, and it lies on a visible face or on a displayed support row.
In this case the witness is the deleted local support row transported to the
common refinement.

Finally apply
\autoref{thm:streamname-finite-cover-support-removal-global-obstruction} on
the refined presentation. The theorem rules out quotient stream equality,
selected limits, countable choice, metric-completeness data, aggregate
formalstatus rows, bridge rows, ambient $\RealUp$ completeness, and replacement
regularity selectors as substitute coordinates. Hence no presentation whose
support agrees after refinement can present the same $\RealUp$
seal-visible source after the row is missing.
\end{proof}

\begin{theorem}[StreamName finite-cover support preservation exactness]
\label{thm:streamname-finite-cover-support-preservation-exactness}
Let $\{Q_i\}_{i \in I}$ and $\{R_k\}_{k \in K}$ be accepted finite covers of
the same current Phase $\RealUp$ and Completion terminal $\StreamNameUp$
request section. Suppose they admit an accepted common refinement
$\{S_\ell\}_{\ell \in L}$, and that on every accepted refined member and
accepted refined overlap the two pullbacks preserve the same $\StreamNameUp$
finite-window row, the same $\DyadicRatCoreUp$ ledger row, the same
$\RegSeqRatUp$ readback row, the same $\RealUp$ seal-visible source, and the
same displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
\NameCert{} support rows. Then the two finite-cover terminal support packets
present the same $\RealUp$ seal-visible source after descent.

The exactness criterion has no further coordinates. It does not assume or
produce quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, ambient $\RealUp$ completeness, or
replacement regularity selectors.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-finite-cover-terminal-support-minimality} to the
accepted common refinement. The accepted terminal support packet is identified
by the four visible faces $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$ together with the displayed $\BHist$,
componentwise $\hsame$, $\Cont$, $\Pkg$, and local \NameCert{} rows on refined
members and overlaps. By hypothesis the two pullbacks preserve exactly these
rows, so their refined support packets expose the same seal-visible source.

It remains to exclude a hidden local defect. Use
\autoref{thm:streamname-finite-cover-terminal-support-defect-localization}
contrapositively: if the descended packets failed to present the same
$\RealUp$ seal-visible source, the failure would be witnessed on some accepted
refined member or accepted refined overlap, and the witness would lie on one
of the displayed visible faces or support rows. Each such row is preserved by
hypothesis, so no such local witness exists.

Finally compare with the negative boundary supplied by
\autoref{thm:streamname-finite-cover-support-invariance-under-refinement}. If
one displayed row were missing, refinement would detect the loss and the same
seal-visible source could not be presented. Since no row is missing, the
complete finite L10 route is precisely the four visible faces
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ with their
displayed local support, and no quotient equality, selected limit, choice
principle, metric-completeness datum, bridge row, ambient completeness
principle, or replacement selector is an extra coordinate.
\end{proof}

\begin{theorem}[StreamName finite-cover support preservation reflection]
\label{thm:streamname-finite-cover-support-preservation-reflection}
Let $\{Q_i\}_{i \in I}$ and $\{R_k\}_{k \in K}$ be accepted finite covers of
the same current Phase $\RealUp$ and Completion terminal $\StreamNameUp$
request section. Suppose they admit an accepted common refinement
$\{S_\ell\}_{\ell \in L}$, and suppose the descended finite-cover terminal
support packets present the same $\RealUp$ seal-visible source. Then, after
pullback to the accepted common refinement, the two presentations agree on
the four visible faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$,
and $\RealUp$, and on the displayed $\BHist$, componentwise $\hsame$,
$\Cont$, $\Pkg$, and local \NameCert{} rows.

The reflection direction has exactly the same boundary as the exactness
direction. It reflects only the finite-cover L10 support rows and does not
reflect quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, aggregate formalstatus rows, ambient
$\RealUp$ completeness, or replacement regularity selectors.
\end{theorem}
\begin{proof}
Argue contrapositively on the accepted common refinement. Suppose that after
pullback the two presentations differ on one of the four visible faces or on
one displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, or local
\NameCert{} row.

By
\autoref{thm:streamname-finite-cover-terminal-support-defect-localization},
the changed or missing displayed row localizes a finite-cover terminal defect
on some accepted refined member or accepted refined overlap. The defect is
not an invisible presentation choice: it lies on one of the rows from which
the refined terminal support packet reads its carrier verdict, classifier
verdict, or consumer-facing terminal route.

Apply
\autoref{thm:streamname-finite-cover-support-removal-global-obstruction} to
that localized support defect. A refined presentation with such a defect
cannot present the same $\RealUp$ seal-visible source merely by deleting,
changing, or omitting the displayed row. The obstruction also rules out
quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, aggregate formalstatus rows, ambient
$\RealUp$ completeness, and replacement regularity selectors as substitute
coordinates for the defective row.

Finally use
\autoref{thm:streamname-finite-cover-support-invariance-under-refinement}.
Passing between the original finite covers and the accepted common refinement
cannot hide the localized defect or convert it into the same descended
$\RealUp$ seal-visible source. Therefore the assumed sameness of the
descended source forces agreement, after pullback, on all four visible faces
and on the displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and
local \NameCert{} rows.

Together with
\autoref{thm:streamname-finite-cover-support-preservation-exactness}, this
gives the bidirectional finite-cover support criterion for the L10
StreamName exit: preserving exactly the displayed finite support yields the
same descended $\RealUp$ source, and the same descended $\RealUp$ source
reflects preservation of exactly that displayed finite support.
\end{proof}

\begin{theorem}[StreamName finite-cover support bicriterion]
\label{thm:streamname-finite-cover-support-bicriterion}
Let $\{Q_i\}_{i \in I}$ and $\{R_k\}_{k \in K}$ be accepted finite covers of
the same current Phase $\RealUp$ and Completion terminal $\StreamNameUp$
request section, and suppose that they admit an accepted common refinement
$\{S_\ell\}_{\ell \in L}$. The descended finite-cover terminal support packets
present the same $\RealUp$ seal-visible source if and only if, after pullback
to the accepted common refinement, the two presentations agree on the four
visible faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$, and on the displayed $\BHist$, componentwise $\hsame$, $\Cont$,
$\Pkg$, and local \NameCert{} rows.

This bicriterion is only a criterion for the finite-cover L10 support surface.
It excludes quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, aggregate formalstatus rows, ambient
$\RealUp$ completeness, and replacement regularity selectors; none of these is
an additional coordinate of the descended support packet, and none is
recovered from the agreement assertion.
\end{theorem}
\begin{proof}
For the forward direction, assume the descended finite-cover terminal support
packets present the same $\RealUp$ seal-visible source. Apply
\autoref{thm:streamname-finite-cover-support-preservation-reflection}. It
reflects that sameness back to agreement, after pullback to the accepted
common refinement, on the four visible faces and on the displayed $\BHist$,
componentwise $\hsame$, $\Cont$, $\Pkg$, and local \NameCert{} rows.

For the reverse direction, assume agreement after pullback on exactly those
visible faces and displayed support rows. Apply
\autoref{thm:streamname-finite-cover-support-preservation-exactness}. The
exactness theorem descends that preserved finite support to the same
$\RealUp$ seal-visible source for the two finite-cover terminal support
packets.

Finally record the boundary of the equivalence. The exactness direction does
not add quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, ambient $\RealUp$ completeness, or
replacement regularity selectors, and the reflection direction does not
reflect quotient stream equality, selected limits, countable choice,
metric-completeness data, bridge rows, aggregate formalstatus rows, ambient
$\RealUp$ completeness, or replacement regularity selectors. Therefore the
criterion binds only the displayed finite-cover support rows and has no hidden
coordinate beyond them.
\end{proof}
