\begin{theorem}[StreamName hub real-completion lattice pointer]
\label{thm:streamname-hub-real-completion-lattice-pointer}
Every public $\StreamNameUp$ hub read used by the Phase Real and Completion route is routed through the sibling chain
$$
\autoref{ch:concrete-instances-rat-namecert}
\longrightarrow
\autoref{ch:concrete-instances-regseqrat-namecert}
\longrightarrow
\autoref{ch:concrete-instances-real-namecert}
$$
and through the local finite-window child theorems of this hub. The route exports only displayed $\BHist$ observations, componentwise $\hsame$ transports, finite $\Cont$ windows, $\Pkg$ provenance, and local $\NameCert$ rows. It exports no quotient stream equality, host sequence equality, selected limit, or ambient completeness row.
\end{theorem}
\begin{proof}
Read the hub as its ordered child surfaces. The carrier definition, certificate fields, finite-window endpoint package, and public interface expose only finite StreamName windows and their local naming rows.

Pass next through the Real and Completion sibling chain. The Rat surface of \autoref{ch:concrete-instances-rat-namecert}, the RegSeqRat surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real surface of \autoref{ch:concrete-instances-real-namecert} are reached through the local handoff and lattice-dependency children already included by the hub.

Use the local finite-window theorems to exhaust the route. The finite-window lattice meet, regular seal non-escape, real seal factorization boundary, and RegSeqRat real lattice dependency rows account for every public read used by the completion-facing consumer.

Since the hub contributes only child rows and no theorem body of its own, no quotient stream equality, host sequence equality, selected limit, or ambient completeness coordinate is exported from the hub read.
\end{proof}
