¥section{StreamName Open-Phase Exit Boundary}
¥label{sec:streamname-open-phase-exit-boundary}

¥begin{theorem}[StreamName open-phase exit boundary]
¥label{thm:streamname-open-phase-exit-boundary}
Every current Phase Real and Completion consumer whose $¥StreamNameUp$ finite-window route reaches the $¥RegSeqRatUp$ readback, the $¥DyadicRatCoreUp$ ledger, and the $¥RealUp$ seal factors through exactly one finite BEDC exit boundary. The boundary is the StreamName window, the RegSeqRat readback, the DyadicRatCore ledger, the RealUp seal, displayed $¥BHist$ observations, componentwise $¥hsame$ transports, displayed $¥Cont$ routes, $¥Pkg$ provenance, and local $¥NameCert$ rows on those finite surfaces.

The boundary exports no quotient stream, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness datum, and no standard bridge row.
¥end{theorem}
¥leanchecked{BEDC.Derived.StreamNameUp.StreamNameOpenPhaseExitBoundary}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-terminal-route}. It places every such Phase Real and Completion consumer on the terminal finite packet and identifies the StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, displayed observations, transports, routes, provenance, and local naming rows.

Next use ¥autoref{thm:streamname-open-phase-terminal-seal-exactness} and ¥autoref{thm:streamname-open-phase-terminal-readback-determinacy}. Terminal seal exactness fixes the four-face route, and readback determinacy says that two consumers with the same four faces and displayed support rows determine the same terminal packet.

Now invoke ¥autoref{thm:streamname-dyadicratcore-window-anchor}. It anchors every StreamName finite-window read consumed by RegSeqRat or by the Real seal through the DyadicRatCore observation and tolerance rows before the regular-rational handoff.

Finally apply ¥autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The open-phase lattice exhausts the public consumer coordinates by the finite route and its displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support. Therefore the exit boundary is exactly that finite BEDC packet, and no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completeness datum, or standard bridge row is exported.
¥end{proof}

¥begin{theorem}[StreamName finite-window exit determinacy]
¥label{thm:streamname-open-phase-finite-window-exit-determinacy}
Let two Phase Real and Completion consumers read accepted $¥StreamNameUp$ exit packets. If they expose the same StreamName finite window, $¥RegSeqRatUp$ readback, $¥DyadicRatCoreUp$ ledger, $¥RealUp$ seal, displayed $¥BHist$ observations, componentwise $¥hsame$ transports, displayed $¥Cont$ routes, $¥Pkg$ provenance, and local $¥NameCert$ rows, then they determine the same finite BEDC exit boundary. Conversely, every accepted exit boundary in this open phase is read through exactly those four faces and their displayed support rows.

The determined boundary carries no quotient stream, host sequence equality, selected limit, ambient $¥RealUp$ completeness row, metric-completeness datum, or standard bridge row.
¥end{theorem}
¥begin{proof}
Start with ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the boundary of every Phase Real and Completion consumer as the finite StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, and the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

For determinacy, use ¥autoref{thm:streamname-open-phase-terminal-seal-exactness} and ¥autoref{thm:streamname-open-phase-terminal-readback-determinacy}. The seal exactness pins the Real-facing coordinate to the same four-face packet, and readback determinacy says that equality of those displayed rows forces equality of the terminal finite packet.

Now apply ¥autoref{thm:streamname-dyadicratcore-window-anchor}. The StreamName window read is anchored through the DyadicRatCore observation and tolerance ledger before RegSeqRat or Real consumers can inspect it.

Finally use ¥autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The lattice gives the converse direction: any accepted open-phase exit boundary is read through the StreamName, RegSeqRat, DyadicRatCore, and Real faces with the displayed support rows only. Since the cited boundaries expose no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completeness datum, or standard bridge row, the finite BEDC packet is the whole exit boundary.
¥end{proof}

¥begin{theorem}[StreamName Real-completion exit certificate]
¥label{thm:streamname-real-completion-exit-certificate}
Every Phase Real and Completion exit read from the current $¥StreamNameUp$ open phase factors through the four finite sibling faces: the StreamName finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, and the $¥RealUp$ seal. The certificate exposes only the displayed rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert
$$
on those four faces, together with the finite window, tolerance, readback, and seal coordinates already named by the open-phase boundary.

The certificate exports no quotient stream, no selected limit, no host sequence equality, no $¥RealUp$ completeness theorem, and no standard bridge row.
¥end{theorem}
¥begin{proof}
First use ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the exit boundary for Phase Real and Completion consumers as the finite StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, and the displayed support rows.

Next apply ¥autoref{thm:streamname-open-phase-terminal-seal-exactness}. The terminal seal makes the Real-facing coordinate exact inside the same finite packet rather than by a selected limit or ambient completeness assertion.

Then use ¥autoref{thm:streamname-dyadicratcore-window-anchor}. The tolerance ledger is pinned to the StreamName finite window before the RegSeqRat and Real consumers can read it.

Finally apply ¥autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The dependency lattice puts the RegSeqRat readback and RealUp seal on the same finite route, so the certificate is exactly the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ packet. Since the component theorems expose no quotient stream, host sequence equality, selected limit, RealUp completeness row, or standard bridge, the packaged exit certificate exports none.
¥end{proof}

¥begin{theorem}[StreamName open-phase four-face terminality]
¥label{thm:streamname-open-phase-four-face-terminality}
Let two Phase Real and Completion exit reads expose the same $¥StreamNameUp$ finite window, the same $¥DyadicRatCoreUp$ tolerance ledger, the same $¥RegSeqRatUp$ readback, the same $¥RealUp$ seal, and the same displayed rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
Then the two reads determine the same terminal finite BEDC route through those four faces. Conversely, any terminal route available to the current open phase is read through exactly the StreamName window, DyadicRatCore ledger, RegSeqRat readback, RealUp seal, and the displayed support rows named above.

The terminal route contains no quotient stream, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness datum, and no standard bridge row.
¥end{theorem}
¥begin{proof}
Begin with ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies every Phase Real and Completion exit boundary with the finite StreamName, RegSeqRat, DyadicRatCore, and Real faces together with their displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support.

Next use ¥autoref{thm:streamname-real-completion-exit-certificate}. The certificate repacks the same four faces as the public exit read, so two reads with matching windows, ledgers, readbacks, seals, and displayed support rows have no remaining coordinate on which their terminal finite routes can differ.

Now apply ¥autoref{thm:streamname-dyadicratcore-window-anchor}. The DyadicRatCore tolerance ledger is anchored to the StreamName finite window before either RegSeqRat readback or RealUp seal can be consumed, which prevents a second tolerance route from entering the terminal packet.

Finally invoke ¥autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The lattice supplies the converse direction by exhausting the open-phase route through the four required faces. Since the cited routes export no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completeness datum, or standard bridge row, terminality belongs to that finite BEDC route alone.
¥end{proof}
¥leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier¥_open¥_phase¥_four¥_face¥_terminality}

¥begin{theorem}[StreamName four-face exit readback]
¥label{thm:streamname-open-phase-four-face-exit-readback}
Every Phase Real and Completion exit read that exposes the $¥StreamNameUp$ finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, the $¥RealUp$ seal, and the displayed support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert
$$
has exactly the finite readback surface named by the open-phase exit boundary. Conversely, every current Phase Real and Completion exit read factors through those four faces and those displayed support rows.

The readback exports no quotient stream, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness datum, and no standard bridge row.
¥end{theorem}
¥leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier¥_open¥_phase¥_four¥_face¥_exit¥_readback}
¥begin{proof}
Begin with ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the public exit surface as the StreamName finite window, the RegSeqRat readback, the DyadicRatCore ledger, the RealUp seal, and the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next apply ¥autoref{thm:streamname-real-completion-exit-certificate}. The certificate places the four faces in one finite packet, so the tolerance ledger, regular-rational readback, and Real-facing seal are read together rather than through an ambient completion object.

Use ¥autoref{thm:streamname-open-phase-four-face-terminality} for the reverse direction. Any terminal route available to the current open phase is already exhausted by the same four faces and displayed support rows.

Finally combine terminal seal exactness with terminal readback determinacy. These references identify matching four-face packets with the same finite readback surface and leave no coordinate for quotient streams, host sequence equality, selected limits, Real completeness, metric completeness, or bridge rows.
¥end{proof}

¥begin{theorem}[StreamName open-phase four-object sufficiency]
¥label{thm:streamname-open-phase-four-object-sufficiency}
The four finite faces
$$
¥DyadicRatCoreUp,¥quad ¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows, are sufficient for the paper-side boundary required by Phase Real and Completion. Any remaining failure belongs to the per-object closurestatus entries or to Lean verification for those four faces, not to a hidden fifth mathematical object.

The sufficient packet contains no quotient stream equality, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
¥end{theorem}
¥leanchecked{BEDC.Derived.StreamNameUp.StreamNameOpenPhaseFourObjectSufficiency}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-exit-boundary} and ¥autoref{thm:streamname-real-completion-exit-certificate}. The boundary theorem names the current Phase Real and Completion consumer surface, and the certificate repacks that surface as the StreamName window, DyadicRatCore ledger, RegSeqRat readback, RealUp seal, and displayed support rows.

Next use ¥autoref{thm:streamname-open-phase-four-face-terminality} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Terminality says that matching four faces and support rows determine the terminal finite route, while readback says that every current exit read is read through exactly those rows.

Finally invoke ¥autoref{thm:streamname-real-completion-four-object-exit-route}. It aligns the same four faces with the roadmap objects $¥DyadicRatCore$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$. Therefore the paper-side exit package is already sufficient for Phase Real and Completion, and any later failure must be read from the individual closurestatus or verification axes rather than from an undisplayed fifth object.
¥end{proof}

¥begin{theorem}[StreamName open-phase Lean touchpoint triad]
¥label{thm:streamname-open-phase-lean-touchpoint-triad}
Every current Phase Real and Completion exit read through the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ is paper-audit-ready exactly along the three existing Lean touchpoints named by the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. This triad exports only the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows already present on those four faces.

The triad adds no Lean marker at this paper site, no quotient stream equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness row, and no standard bridge row.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. It says that the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$, together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows, already suffice for the current Phase Real and Completion boundary.

Next use ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. The readback theorem fixes every current exit read on exactly those four faces and displayed support rows, so the paper audit has no hidden fifth object to inspect.

Finally invoke ¥autoref{thm:streamname-real-completion-four-object-exit-route}. It aligns the same boundary with the roadmap route. The existing machine-side route is then the three-touchpoint path named in Lean as ¥texttt{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier¥_singleton¥_diagonal¥_handoff}, ¥texttt{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier¥_regseqrat¥_bridge¥_handoff¥_exactness}, and ¥texttt{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier¥_real¥_seal¥_handoff}. These names identify the future formalization route only; they do not create a current paper marker or export quotient equality, selected limits, ambient completeness, metric completeness, or a standard bridge row.
¥end{proof}

¥begin{theorem}[StreamName Real-completion exit Lean route boundary]
¥label{thm:streamname-real-completion-exit-lean-route-boundary}
Every current Phase Real and Completion four-face exit read consumes machine support only through the three primary paper sites already carrying the route markers: the StreamName singleton finite-window handoff of ¥autoref{thm:streamname-regseqrat-singleton-diagonal-handoff}, the DyadicRatCore RegSeqRat bridge handoff exactness of ¥autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness}, and the RegSeqRat Real seal handoff of ¥autoref{thm:regseqrat-real-seal-handoff}. Equivalently, the route uses
$$
¥begin{gathered}
¥texttt{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier¥_singleton¥_diagonal¥_handoff},¥¥
¥texttt{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier¥_regseqrat¥_bridge¥_handoff¥_exactness},¥¥
¥texttt{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier¥_real¥_seal¥_handoff}
¥end{gathered}
$$
only at those primary sites.

This paper site records the route boundary but adds no additional Lean marker. It exports no quotient stream equality, selected limit, ambient $¥RealUp$ completeness, metric-completeness datum, countable choice, or bridge row.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. It fixes the current exit packet as the four displayed faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ together with the visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows.

Next use ¥autoref{thm:streamname-open-phase-lean-touchpoint-triad}. The triad says that the machine-facing support of that packet is exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

Finally invoke ¥autoref{thm:streamname-real-completion-four-object-exit-route}. It identifies the same four-face packet as the Phase Real and Completion route, while the primary markers are already attached at ¥autoref{thm:streamname-regseqrat-singleton-diagonal-handoff}, ¥autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness}, and ¥autoref{thm:regseqrat-real-seal-handoff}. Therefore this boundary site can only point to those primary sites and cannot create a second marker or an extra coordinate for quotient streams, selected limits, ambient completeness, metric completeness, countable choice, or bridge data.
¥end{proof}

¥begin{theorem}[StreamName Real-completion exit obligation ledger]
¥label{thm:streamname-real-completion-exit-obligation-ledger}
The current Phase Real and Completion exit obligation ledger is exactly the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ together with displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support. The ledger has no separate aggregate object beyond those four faces and their support rows.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-exit-boundary} and ¥autoref{thm:streamname-real-completion-exit-certificate}. These theorems name the exit packet as the finite StreamName window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, and the displayed support rows.

Next use ¥autoref{thm:streamname-open-phase-four-face-terminality} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Terminality fixes the route once the four faces and support rows agree, while readback says that every current exit read is consumed through those rows.

Finally apply ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The Lean-facing route is confined to the existing primary touchpoints for the StreamName finite window, DyadicRatCore RegSeqRat handoff, and RegSeqRat Real seal. Hence the paper obligation ledger is exactly the four displayed faces with $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support.
¥end{proof}

¥begin{theorem}[StreamName open-phase Lean route totality]
¥label{thm:streamname-open-phase-lean-route-totality}
Every current Phase Real and Completion exit read through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ is machine-facing exactly through the three primary Lean touchpoints named in ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. Thus the current route is exhausted by the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Any consumer that needs further machine support has left the current open-phase exit ledger.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-real-completion-exit-obligation-ledger}. It fixes the current ledger as the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows.

Next use ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary} and ¥autoref{thm:streamname-open-phase-lean-touchpoint-triad}. These identify the machine-facing route of that ledger with exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

Finally invoke ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. Since the four listed faces already suffice for the current Phase Real and Completion boundary, a consumer asking for another machine support row is no longer reading the displayed open-phase exit ledger. The theorem adds no marker and asserts no quotient stream, selected limit, completeness row, countable-choice row, or bridge row.
¥end{proof}

¥begin{theorem}[StreamName Real-completion touchpoint minimality]
¥label{thm:streamname-real-completion-touchpoint-minimality}
A current Phase Real and Completion exit read is paper-audit-complete if and only if it exposes exactly the four paper faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$, and its machine-facing support is confined to the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

Equivalently, the paper audit surface is precisely the four-face ledger named by ¥autoref{thm:streamname-open-phase-four-object-sufficiency}, while the machine route is precisely the three-touchpoint route named by ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary} and exhausted by ¥autoref{thm:streamname-open-phase-lean-route-totality}. The complete read contains no quotient stream equality, selected limit, ambient $¥RealUp$ completeness row, metric-completeness datum, countable-choice row, or standard bridge row.
¥end{theorem}
¥begin{proof}
For the forward direction, start from a paper-audit-complete current exit read. Apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency} to identify the paper surface with exactly the four displayed faces and their visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Then use ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. It confines the machine-facing support to the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Finally apply ¥autoref{thm:streamname-open-phase-lean-route-totality}; any requested machine coordinate outside those three sites leaves the current open-phase exit ledger.

For the reverse direction, assume the read exposes the four faces and only the three named machine touchpoints. The four-face sufficiency theorem supplies the paper audit packet, while the Lean-route boundary supplies the complete machine-facing route for that packet.

The route-totality theorem rules out missing support inside the current exit read. Since neither the four-face packet nor the three-touchpoint route has a coordinate for quotient stream equality, selected limits, ambient completeness, metric-completeness data, countable choice, or standard bridge rows, the read is paper-audit-complete exactly at the displayed boundary.
¥end{proof}

¥begin{theorem}[StreamName Real-completion objectwise status completeness]
¥label{thm:streamname-real-completion-objectwise-status-completeness}
A current Phase Real and Completion exit read through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ is status-complete exactly when it exposes those four faces, confines machine support to the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff, and also reads the four local face closurestatus, formalstatus, leantarget, and bridgestatus rows objectwise.

Equivalently, the three-touchpoint route is necessary for the machine-facing side of the current roadmap exit certificate, but it is not by itself sufficient for the roadmap exit certificate. The certificate is complete only when the four local face-status records are present alongside the displayed finite support rows $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$.

The status-complete read contains no quotient stream equality, selected limit, ambient $¥RealUp$ completeness row, metric-completeness datum, countable-choice row, aggregate formalstatus row, aggregate bridge row, or standard bridge row.
¥end{theorem}
¥begin{proof}
First identify the underlying exit surface. By ¥autoref{thm:streamname-real-completion-touchpoint-minimality}, the current paper audit surface exposes exactly the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$, while the machine-facing support is confined to the three named touchpoints.

Next exhaust the route. Apply ¥autoref{thm:streamname-real-completion-exit-obligation-ledger} to keep the obligation ledger on the four faces and the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows. Apply ¥autoref{thm:streamname-open-phase-lean-route-totality} to rule out any further machine coordinate inside the current open-phase ledger.

It remains to read the roadmap exit certificate on its own axes. The roadmap discipline of ¥autoref{sec:roadmap-closure-and-verification-axes} and the Phase Real and Completion exit criterion of ¥autoref{sec:roadmap-near-term-phases} require the four objects to be read locally on independent closure and verification axes. By ¥autoref{thm:real-l10-objectwise-face-status-exit}, that read is the objectwise product of the four local closurestatus, formalstatus, leantarget, and bridgestatus records, together with the displayed finite support rows.

Therefore the three-touchpoint route is necessary for the machine-facing support, but it cannot replace the four local status rows. Conversely, when the four faces, the three touchpoints, and the four objectwise status records are all present, the same cited results supply exactly the current Phase Real and Completion exit certificate.

Finally exclude substitute coordinates. The touchpoint-minimality theorem and the Real-side objectwise face-status theorem jointly leave no coordinate for quotient stream equality, selected limits, ambient $¥RealUp$ completeness, metric-completeness data, countable choice, aggregate formalstatus rows, aggregate bridge rows, or standard bridge rows.
¥end{proof}

¥begin{theorem}[StreamName open-phase four-face scope exactness]
¥label{thm:streamname-open-phase-four-face-scope-exactness}
Any current Phase Real and Completion route that exposes the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ has no fifth object. In particular it does not contain a quotient stream, selected limit, ambient $¥RealUp$ completeness object, metric-completeness datum, countable-choice row, or standard bridge row.
¥end{theorem}
¥begin{proof}
Begin with ¥autoref{thm:streamname-open-phase-four-face-terminality}. Once the four faces and their displayed support rows are fixed, the terminal finite route is determined.

Use ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. It reads every current exit through the same four local faces, so any proposed fifth object would have to appear in that readback surface.

Now apply ¥autoref{thm:streamname-real-completion-exit-certificate} and ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The certificate and machine-route boundary list only the finite window, dyadic ledger, RegSeqRat readback, Real seal, and the three existing primary machine touchpoints. None of those rows is a quotient stream, selected limit, ambient completeness object, metric-completeness datum, countable-choice row, or standard bridge.
¥end{proof}

¥begin{theorem}[StreamName Real-RegSeqRat dyadic window pullback]
¥label{thm:streamname-real-regseqrat-dyadic-window-pullback}
The $¥RealUp$ seal and the $¥RegSeqRatUp$ readback in the current Phase Real and Completion exit share the same $¥DyadicRatCoreUp$ tolerance ledger through the finite $¥StreamNameUp$ window. Thus any exit read that preserves the Real seal and the RegSeqRat readback pulls back to the same dyadic tolerance window, rather than to a selected limit, quotient stream, host equality, ambient completeness theorem, or bridge coordinate.
¥end{theorem}
¥begin{proof}
First use ¥autoref{thm:streamname-real-completion-exit-certificate}. It displays the Real seal and RegSeqRat readback in the same certificate as the finite StreamName window and DyadicRatCore tolerance ledger.

Next apply ¥autoref{thm:streamname-open-phase-four-face-terminality} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. These results force both reads through the same four-face terminal packet, so the $¥RealUp$ and $¥RegSeqRatUp$ faces cannot select different dyadic ledgers once the StreamName finite window is fixed.

Finally invoke ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The machine-facing support is exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Those touchpoints align the dyadic tolerance ledger with the finite window and provide no coordinate for selected limits, quotient streams, host equality, ambient completeness, or bridge data.
¥end{proof}

¥begin{theorem}[StreamName Real-completion four-face terminal pullback]
¥label{thm:streamname-real-completion-four-face-terminal-pullback}
Let $X$ and $Y$ be current Phase Real and Completion exit reads. Suppose both reads expose the same $¥StreamNameUp$ finite window, the same $¥DyadicRatCoreUp$ tolerance ledger, the same $¥RegSeqRatUp$ readback, the same $¥RealUp$ seal, and the same displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows. Then $X$ and $Y$ pull back to the same terminal finite BEDC route.

No quotient stream, selected limit, host equality, ambient completeness theorem, metric-completeness datum, choice row, or bridge row can distinguish the two reads once those four faces and displayed support rows agree.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. It identifies the current Phase Real and Completion boundary with exactly the four objects $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ together with the visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next use ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Every current exit read is read through precisely those four faces and support rows, so the hypotheses on $X$ and $Y$ place them on the same finite readback surface.

Finally apply ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The machine-facing route is confined to the three primary touchpoints already attached to the StreamName finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Since those touchpoints carry no quotient, limit-selection, host-equality, completeness, choice, or bridge coordinate, the two reads determine the same terminal finite BEDC route.
¥end{proof}

¥begin{theorem}[StreamName four-face Lean route consistency]
¥label{thm:streamname-four-face-lean-route-consistency}
Every current four-face exit read through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ consumes machine support only through the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Conversely, those three touchpoints cover exactly the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows of the paper route through the four faces.

This consistency statement adds no Lean marker at this paper site. It does not claim quotient streams, selected limits, ambient $¥RealUp$ completeness, metric completeness, countable choice, or standard bridge status.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the current open-phase exit boundary with the finite StreamName window, DyadicRatCore ledger, RegSeqRat readback, Real seal, and displayed support rows.

Next use ¥autoref{thm:streamname-open-phase-four-object-sufficiency} and ¥autoref{thm:streamname-open-phase-four-face-terminality}. These theorems say that the four faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ suffice for the current exit packet and that matching those faces with their support rows determines the terminal route.

Now apply ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The machine-facing support route is confined to the three named touchpoints: the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

For the converse direction, read those same touchpoints back along the four-face terminal packet. The StreamName handoff covers the finite-window face, the DyadicRatCore handoff covers the dyadic ledger and bridge face, and the RegSeqRat handoff covers the Real seal face; together with the terminality and sufficiency results, these are exactly the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows of the paper route. No additional machine support coordinate remains in the open-phase boundary.
¥end{proof}

¥begin{theorem}[StreamName open-phase facewise record completeness]
¥label{thm:streamname-open-phase-facewise-record-completeness}
A Phase Real and Completion exit read through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ is complete as a $¥StreamNameUp$-side boundary exactly when the four canonical local face records are displayed separately: the $¥DyadicRatCoreUp$ tolerance-ledger status, the $¥StreamNameUp$ finite-window status, the $¥RegSeqRatUp$ readback and seal status, and the $¥RealUp$ seal status. These are the local records attached to the four displayed faces, not a composite route token.

For the reverse direction, the only machine-route sites used are the three primary sites already named by ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. No aggregate formalstatus token, aggregate bridge, selected limit, quotient stream, ambient completeness theorem, countable-choice row, or metric-completeness datum can replace a missing face record.
¥end{theorem}
¥begin{proof}
For the forward direction, apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. It says that the current Phase Real and Completion boundary is exhausted by the four displayed faces together with the visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows.

Next use ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. The readback theorem identifies every current exit read with exactly those four faces and their displayed support rows. Thus audit completeness can only be checked componentwise, by reading the StreamName, DyadicRatCore, RegSeqRat, and Real records that already belong to the packet.

For the reverse direction, assume that the four canonical local face records are displayed separately. Apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency} to identify the packet with exactly the $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ faces and their visible support rows.

Next apply ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. It reads every current exit through those same four face records, so the displayed local rows cover the StreamName-side boundary rather than merely a downstream summary of it.

Finally apply ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. That theorem restricts the reverse route to the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff; those are precisely the primary machine-route sites already attached to the four local records. The roadmap two-axis discipline is used only to keep the four local theory and verification reports from collapsing into one token. Hence no aggregate formalstatus token, aggregate bridge, selected limit, quotient stream, ambient completeness theorem, countable-choice row, or metric-completeness datum can repair an absent face record.
¥end{proof}

¥begin{theorem}[StreamName--Real open-phase facewise audit correspondence]
¥label{thm:streamname-real-open-phase-facewise-audit-correspondence}
A current Phase Real and Completion exit read is complete as a $¥StreamNameUp$-side facewise record exactly when it satisfies the $¥RealUp$-side facewise audit obstruction. Both conditions require the same four local records for $¥DyadicRatCoreUp$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$, together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Thus the StreamName-side open-phase completeness criterion and the Real-side L10 audit obstruction name the same componentwise four-face boundary. No aggregate formalstatus token, bridge row, completeness row, quotient stream, selected limit, or host equality row is part of this correspondence.
¥end{theorem}
¥begin{proof}
For the StreamName-to-Real direction, apply ¥autoref{thm:streamname-open-phase-facewise-record-completeness}. A complete StreamName-side read already displays the DyadicRatCore tolerance-ledger record, the StreamName finite-window record, the RegSeqRat readback and seal record, and the Real seal record as separate local rows.

Next use ¥autoref{thm:real-l10-exit-facewise-audit-obstruction} and ¥autoref{thm:real-l10-four-face-audit-clean-handoff}. The Real-side obstruction asks for exactly those four local records and refuses any aggregate audit substitute. Since the visible support rows are the same $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows, the StreamName-side complete read satisfies the Real-side audit condition.

For the Real-to-StreamName direction, start from the Real-side facewise audit condition. It supplies the four local audit records separately, so ¥autoref{thm:streamname-open-phase-four-object-sufficiency} identifies the current open-phase packet with the same $¥DyadicRatCoreUp$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$ faces and their displayed support rows.

Finally apply ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The only machine-facing route available to this packet is the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. These are the route sites already attached to the same four local records, so the Real-side audit condition gives the StreamName-side facewise record completeness.

The last sentence of the theorem is the common boundary condition, not an extra certificate. The cited results leave no coordinate for an aggregate formalstatus token, bridge row, completeness row, quotient stream, selected limit, or host equality row.
¥end{proof}

¥begin{theorem}[StreamName budgeted real window handoff totality]
¥label{thm:streamname-budgeted-real-window-handoff-totality}
Every accepted $¥BudgetedRealSealRouteUp$ consumer of a $¥StreamNameUp$ finite-window exit read factors through the displayed handoff rows
$$
¥StreamNameUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp,¥quad ¥RealWindowBudgetUp,¥quad ¥BudgetedRealSealRouteUp
$$
together with only the support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
The factorization is total for such consumers: the $¥StreamNameUp$ finite window is first read through the four local face records, then through the $¥RealWindowBudgetUp$ packet, and finally through the $¥BudgetedRealSealRouteUp$ carrier and local $¥NameCert$ surface.

No selected limit, quotient stream, ambient $¥RealUp$ completeness row, countable-choice row, metric-completeness datum, host equality row, or standard bridge row is part of this consumer handoff.
¥end{theorem}
¥begin{proof}
Start with ¥autoref{thm:streamname-open-phase-facewise-record-completeness}. It gives the $¥StreamNameUp$-side exit read as four separately displayed local records: the StreamName finite window, the DyadicRatCore tolerance ledger, the RegSeqRat readback and seal status, and the RealUp seal status.

Next apply ¥autoref{thm:streamname-real-window-budget-pullback} and ¥autoref{thm:streamname-open-phase-budget-consumer-terminality}. The pullback places every accepted $¥RealWindowBudgetUp$ consumer over the same finite request, window, dyadic, regularity, and Real seal rows, while terminality prevents any further discriminator once those rows and the displayed support rows agree.

Now use ¥autoref{thm:real-window-budget-real-completion-handoff}. The $¥RealWindowBudgetUp$ packet therefore hands the finite StreamName window, dyadic readbacks, RegSeqRat handoff, and Real seal to the Real-facing completion route without adding a selected limit, quotient stream, or ambient completeness coordinate.

Finally read the $¥BudgetedRealSealRouteUp$ carrier and NameCert obligations of ¥autoref{def:budgeted-real-seal-route-carrier} and ¥autoref{thm:budgeted-real-seal-route-namecert-obligations}. Its accepted packet consumes the displayed selector, threshold, observation-budget, limit-seal, Real readback, transport, continuation, provenance, and local naming rows; along the StreamName exit boundary these are reached only through the already displayed $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, $¥RealUp$, and $¥RealWindowBudgetUp$ rows. The non-escape theorem ¥autoref{thm:budgeted-real-seal-route-nonescape} then excludes host equality, selected limits, quotient streams, ambient completeness, countable choice, metric-completeness data, and standard bridge rows from the handoff.
¥end{proof}

¥begin{theorem}[StreamName open-phase budget route lock]
¥label{thm:streamname-open-phase-budget-route-lock}
Any accepted $¥BudgetedRealSealRouteUp$ consumer whose finite window is read through $¥StreamNameUp$ factors through the same four-face open-phase exit boundary
$$
¥StreamNameUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
with only $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows. The budgeted route is therefore a consumer of the boundary, not a fifth Real-completion object, and it cannot smuggle quotient streams, selected limits, host real equality, ambient completeness, countable choice, or metric-completeness data into the exit packet.
¥end{theorem}
¥begin{proof}
Start with the open-phase exit boundary, ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the current Real-completion exit with the StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat regularity readback, RealUp seal, and the visible support rows.

Next use budgeted real window handoff totality, ¥autoref{thm:streamname-budgeted-real-window-handoff-totality}. It already routes an accepted $¥BudgetedRealSealRouteUp$ consumer through the four local faces, the $¥RealWindowBudgetUp$ packet, and only $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support.

Finally read the budgeted route selector, TailMeet threshold, Real-seal readback, and non-escape theorems from ¥autoref{ch:concrete-instances-budgeted-real-seal-route-namecert}. The selector and threshold rows feed the route into the RealObservationBudget and CauchyLimitSeal handoff, while the Real readback and non-escape rows prevent a separate completion object or hidden stream source from appearing.
¥end{proof}

¥begin{theorem}[StreamName open-phase local status nonescape]
¥label{thm:streamname-open-phase-local-status-nonescape}
For any current Phase Real and Completion exit read through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$, suppose one of the four local face status records is absent: the $¥DyadicRatCoreUp$ tolerance-ledger status, the $¥StreamNameUp$ finite-window status, the $¥RegSeqRatUp$ readback and seal status, or the $¥RealUp$ seal status. Then the absent local record is not supplied by any aggregate formalstatus token, aggregate bridge row, selected limit, quotient stream, ambient completeness theorem, countable-choice row, metric-completeness datum, or standard bridge row.

Equivalently, the current open-phase exit boundary has no escape route from a missing local face record to a route-level verification or bridge coordinate. Each of the four objects must display its own local status row before the $¥StreamNameUp$-side boundary is complete.
¥end{theorem}
¥begin{proof}
Start with ¥autoref{thm:streamname-open-phase-facewise-record-completeness}. It identifies boundary completeness with the four canonical local records displayed separately, so an absent DyadicRatCore, StreamName, RegSeqRat, or Real record is already a failure at the objectwise status surface.

Next apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Sufficiency says that the current exit packet has only the four displayed objects and their visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows. Readback says that every current exit read is read through exactly those four local faces.

Now use ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The only machine-facing route available to the current read is the three primary touchpoints already attached to the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Those touchpoints can report the route they occupy, but they do not manufacture a missing local status row for any face.

Finally exhaust the possible substitutes. The four-face route has no quotient stream, selected limit, ambient completeness theorem, countable-choice row, metric-completeness datum, or standard bridge row by the cited boundary results. Aggregate formalstatus and bridge prose therefore remain summaries of displayed local records, not replacements for one of them.
¥end{proof}

¥begin{theorem}[StreamName open-phase local-status exit lock]
¥label{thm:streamname-open-phase-local-status-exit-lock}
A current Phase Real and Completion exit read is accepted at the $¥StreamNameUp$ side exactly when the four local status records are present together: the $¥StreamNameUp$ finite-window status, the $¥DyadicRatCoreUp$ tolerance-ledger status, the $¥RegSeqRatUp$ readback and seal status, and the $¥RealUp$ seal status. The four records must be matched to the same displayed support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
When those four records and those support rows agree, they jointly determine the current exit route through the terminal four-face packet. When one record is absent or mismatched, the route is not accepted as the current $¥StreamNameUp$-side exit read.

This lock is local to the open-phase boundary. It does not introduce quotient streams, selected limits, ambient $¥RealUp$ completeness, metric-completeness data, countable choice, aggregate formalstatus rows, or aggregate bridge rows.
¥end{theorem}
¥begin{proof}
For necessity, apply ¥autoref{thm:streamname-open-phase-facewise-record-completeness}. It says that boundary completeness is exactly the separate display of the $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ local status records over the visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next use ¥autoref{thm:streamname-open-phase-local-status-nonescape}. If any one of the four local records is absent, no route-level status token, bridge row, selected limit, quotient stream, completeness datum, or countable-choice row can replace it. Thus every accepted current exit read must carry all four local records.

For sufficiency, apply ¥autoref{thm:streamname-open-phase-terminal-classifier-exactness}. Once the four face records and the displayed support rows match, public acceptance factors through the terminal four-face classifier surface and has no further coordinate.

Finally apply ¥autoref{thm:streamname-open-phase-four-face-normal-form}. It identifies the accepted route with the unique normal-form packet consisting of the StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, and the same support rows. Hence the four local records jointly determine the current exit route, while the excluded quotient, limit, completeness, choice, aggregate status, and bridge rows remain outside the packet.
¥end{proof}

¥begin{theorem}[StreamName open-phase handoff terminal cover]
¥label{thm:streamname-open-phase-handoff-terminal-cover}
Every current Phase Real and Completion handoff that reaches the $¥StreamNameUp$ finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, and the $¥RealUp$ seal is covered by the terminal finite BEDC packet displayed in this section. The cover is exactly the four faces
$$
¥StreamNameUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

The cover exports no quotient stream, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
¥end{theorem}
¥begin{proof}
Begin with ¥autoref{thm:streamname-open-phase-exit-boundary}. It identifies the public handoff boundary with the finite StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, and the displayed support rows.

Next apply ¥autoref{thm:streamname-real-completion-exit-certificate}. The certificate repacks the same boundary as the four-face packet, so the StreamName window, tolerance ledger, readback, and seal are read as one finite BEDC surface.

Use ¥autoref{thm:streamname-open-phase-four-face-terminality} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Terminality says that matching four faces and support rows determine the terminal finite route, while readback says that every current exit read is already read through exactly those rows.

Finally combine ¥autoref{thm:streamname-open-phase-four-object-sufficiency} with ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The sufficiency theorem aligns the packet with the open construction order, and the machine-touchpoint boundary restricts the route to the named primary sites. Therefore every current handoff reaching those four faces is covered by the displayed terminal packet, with no additional quotient, host equality, selected limit, completeness, choice, or bridge coordinate.
¥end{proof}

¥begin{theorem}[StreamName open-phase terminal classifier exactness]
¥label{thm:streamname-open-phase-terminal-classifier-exactness}
A current Phase Real and Completion read is publicly accepted exactly when its $¥StreamNameUp$ finite window, $¥DyadicRatCoreUp$ tolerance ledger, $¥RegSeqRatUp$ readback, $¥RealUp$ seal, and displayed rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert
$$
factor through the terminal four-face classifier surface for the open phase.

Equivalently, public acceptance has no further coordinate beyond that terminal classifier packet: no quotient stream equality, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
¥end{theorem}
¥begin{proof}
For necessity, start with ¥autoref{thm:streamname-open-phase-four-face-terminality} and ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Terminality identifies the finite route determined by the four faces and displayed support rows, while readback says every current Phase Real and Completion exit read is read through exactly those faces and rows.

Next apply ¥autoref{thm:streamname-real-completion-four-object-exit-route}. It aligns the same StreamName window, DyadicRatCore ledger, RegSeqRat readback, and RealUp seal with the current Real-completion exit route, so the open-phase terminal route is the four-object route already used by Phase Real and Completion.

For sufficiency, use ¥autoref{thm:streamname-real-completion-classifier-pullback}. Once the four faces and displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows factor through that classifier surface, the public read is determined componentwise by the same finite packet.

Finally invoke ¥autoref{thm:streamname-real-completion-dependency-exactness}. Dependency exactness says that the four dependency faces with the displayed support rows are precisely the public acceptance boundary, and it excludes quotient stream equality, host sequence equality, selected limits, ambient completeness, metric-completeness data, countable choice, and standard bridge rows. Hence public acceptance is exact for the terminal four-face classifier surface and for no larger object.
¥end{proof}

¥begin{theorem}[StreamName open-phase four-face ledger exactness]
¥label{thm:streamname-open-phase-four-face-ledger-exactness}
For every current Phase Real and Completion read accepted through the $¥StreamNameUp$ finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, the $¥RealUp$ seal, and the displayed rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert,
$$
the ledger coordinate is exactly the finite four-face ledger already exposed by those rows. Equivalently, any $¥RealWindowBudgetUp$ consumer can project the ledger from the four faces themselves, and any hidden compression, selected limit, quotient stream, host sequence equality, ambient $¥RealUp$ completeness row, metric-completeness row, countable-choice row, or standard bridge row lies outside the accepted packet.
¥end{theorem}
¥begin{proof}
First apply ¥autoref{thm:streamname-open-phase-terminal-classifier-exactness}. It identifies public acceptance with the terminal four-face classifier surface over the StreamName window, DyadicRatCore ledger, RegSeqRat readback, Real seal, and displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. The current boundary has only the four objects $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ as its exposed mathematical faces, so the ledger coordinate cannot be supplied by a fifth object or an undisplayed completion row.

Now use ¥autoref{thm:streamname-real-completion-exit-lean-route-boundary}. The machine-facing support route is confined to the three primary sites already attached to the StreamName finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff, and the RegSeqRat Real seal handoff; this theorem adds no marker here and contributes no extra ledger coordinate.

Finally read the downstream budget surface. By ¥autoref{def:real-window-budget-carrier} and ¥autoref{thm:real-window-budget-real-completion-handoff}, a $¥RealWindowBudgetUp$ packet projects its finite StreamName window, dyadic readbacks, RegSeqRat handoff, and Real seal from the same displayed route. Thus the accepted packet exposes exactly the four-face ledger consumed downstream, and hidden compression, selected limits, quotient streams, host equality, ambient completeness, metric completeness, countable choice, and standard bridge data remain outside the packet.
¥end{proof}

¥begin{theorem}[StreamName open-phase four-face normal form]
¥label{thm:streamname-open-phase-four-face-normal-form}
Every accepted Phase Real and Completion exit read has a unique normal form at the terminal finite BEDC route. The normal form consists exactly of the $¥StreamNameUp$ finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, the $¥RealUp$ seal, and the displayed support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$

Conversely, any packet whose exposed coordinates are exactly those four faces and those support rows is accepted by the terminal classifier surface for the open phase.

The normal form has no quotient stream equality, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness datum, no countable-choice row, and no standard bridge row.
¥end{theorem}
¥begin{proof}
For existence, apply ¥autoref{thm:streamname-open-phase-four-object-sufficiency}. It identifies the current Phase Real and Completion boundary with the four displayed faces $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$ together with the visible $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next apply ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. Every accepted exit read is read through those same faces and rows, so the displayed packet is a normal-form representative of the current open-phase exit read rather than a downstream summary.

For uniqueness, use ¥autoref{thm:streamname-open-phase-terminal-classifier-exactness}. Public acceptance is exact for the terminal four-face classifier surface, so two accepted packets with the same four faces and support rows determine the same terminal finite BEDC route.

For the converse direction, apply ¥autoref{thm:streamname-open-phase-four-face-ledger-exactness}. A packet exposing exactly the StreamName window, DyadicRatCore ledger, RegSeqRat readback, Real seal, and displayed support rows already supplies the ledger coordinate consumed by the terminal classifier surface.

Finally exhaust the excluded coordinates. The same cited theorems leave no place for quotient stream equality, host sequence equality, selected limits, ambient $¥RealUp$ completeness, metric-completeness data, countable choice, or standard bridge data. Therefore the four-face packet is the canonical Phase Real and Completion exit object, and any packet with precisely those coordinates is accepted by the terminal classifier surface.
¥end{proof}

¥begin{theorem}[StreamName Real-window budget pullback]
¥label{thm:streamname-real-window-budget-pullback}
Any accepted $¥StreamNameUp$ finite-window exit read consumed by a $¥RealWindowBudgetUp$ packet factors through the same finite request, $¥StreamNameUp$ window rows, $¥DyadicRatCoreUp$ readbacks, $¥RegSeqRatUp$ handoff, $¥RealUp$ seal, componentwise $¥hsame$ transports, displayed $¥Cont$ route, $¥Pkg$ provenance, and local $¥NameCert$ row. Conversely, every accepted $¥RealWindowBudgetUp$ packet exposes a $¥StreamNameUp$ finite-window face through its displayed window rows.

The pullback adds no quotient stream, host sequence equality, selected limit, ambient $¥RealUp$ completeness row, metric-completeness datum, countable-choice row, or standard bridge row.
¥end{theorem}
¥begin{proof}
For the forward direction, apply ¥autoref{thm:streamname-open-phase-terminal-classifier-exactness}. It identifies accepted open-phase reads with the terminal four-face classifier surface over the StreamName window, DyadicRatCore ledger, RegSeqRat readback, Real seal, and displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next read the $¥RealWindowBudgetUp$ carrier of ¥autoref{def:real-window-budget-carrier}. Its request, window, dyadic, handoff, seal, selector, disclosure, transport, continuation, provenance, and local naming rows are precisely the finite route available to a Real-window budget consumer.

For the reverse direction, project an accepted $¥RealWindowBudgetUp$ packet onto its $V$ coordinate. By the carrier definition and the Real-completion handoff of ¥autoref{thm:real-window-budget-real-completion-handoff}, $V$ is the StreamName finite-window face of the same packet.

Finally compose with the sibling budget surfaces. The selector stability of ¥autoref{thm:real-window-budget-selector-stability}, the CauchyDiagonalBudget surface of ¥autoref{ch:concrete-instances-cauchydiagonalbudget-namecert}, and the RealObservationBudget disclosure route of ¥autoref{ch:concrete-instances-real-observation-budget-namecert} keep the pullback on the same finite request and support rows. Since none of these surfaces carries quotient streams, host equality, selected limits, ambient completeness, metric completeness, countable choice, or a standard bridge, the pullback exports none.
¥end{proof}

¥begin{theorem}[StreamName open-phase budget-consumer terminality]
¥label{thm:streamname-open-phase-budget-consumer-terminality}
Every accepted $¥RealWindowBudgetUp$ consumer of a $¥StreamNameUp$ finite-window exit read determines the same terminal four-face route through $¥StreamNameUp$, $¥DyadicRatCoreUp$, $¥RegSeqRatUp$, and $¥RealUp$. The route is read only through the displayed rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
Once two such consumers agree on their budget rows, no quotient stream, selected limit, host equality, ambient completeness theorem, countable-choice row, metric-completeness datum, or standard bridge row can distinguish them.
¥end{theorem}
¥begin{proof}
Begin with the pullback of ¥autoref{thm:streamname-real-window-budget-pullback}. It says that every accepted budget consumer of the StreamName finite-window exit read factors through the finite request, StreamName window rows, DyadicRatCore readbacks, RegSeqRat handoff, Real seal, componentwise $¥hsame$ transports, displayed $¥Cont$ route, $¥Pkg$ provenance, and local $¥NameCert$ row.

Next apply ¥autoref{thm:streamname-open-phase-terminal-classifier-exactness} and ¥autoref{thm:streamname-real-completion-four-object-exit-route}. The classifier exactness theorem makes the accepted open-phase read terminal over the displayed four faces, and the four-object exit route identifies those faces as the StreamName, DyadicRatCore, RegSeqRat, and RealUp route already used by Phase Real and Completion.

Finally read the budget carrier. By ¥autoref{def:real-window-budget-carrier} and ¥autoref{thm:real-window-budget-real-completion-handoff}, a $¥RealWindowBudgetUp$ consumer exposes its Real-facing route as the same finite chain from the StreamName window through dyadic readback and regular handoff to the Real seal. Thus agreement on the displayed budget rows leaves only that terminal four-face route, while quotient streams, selected limits, host equality, ambient completeness, choice, metric completeness, and standard bridge data remain outside the accepted packet.
¥end{proof}

¥begin{theorem}[StreamName open-phase exit route completeness]
¥label{thm:streamname-open-phase-exit-route-completeness}
A current Phase Real and Completion exit packet is accepted exactly when it is a terminal finite route through the $¥StreamNameUp$ finite window, the $¥DyadicRatCoreUp$ tolerance ledger, the $¥RegSeqRatUp$ readback, the $¥RealUp$ seal, and the displayed support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
Equivalently, every accepted packet exposes precisely those four L10 faces and those rows, and conversely any packet exposing exactly those coordinates is accepted by the terminal open-phase classifier surface.

The route has no quotient stream equality, no host sequence equality, no selected limit, no ambient $¥RealUp$ completeness row, no metric-completeness datum, no countable-choice row, and no standard bridge row.
¥end{theorem}
¥begin{proof}
For necessity, apply ¥autoref{thm:streamname-open-phase-four-face-normal-form}. It identifies every accepted Phase Real and Completion exit read with the normal-form packet consisting of the StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, and displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Next use ¥autoref{thm:streamname-open-phase-four-face-ledger-exactness}. The tolerance-ledger coordinate is not an external budget summary; it is the finite ledger already exposed by the four faces and their support rows.

Then pull the downstream consumer back by ¥autoref{thm:streamname-real-window-budget-pullback}. Any $¥RealWindowBudgetUp$ consumer of the StreamName finite-window exit read factors through the same finite request, window rows, dyadic readbacks, RegSeqRat handoff, Real seal, componentwise transports, continuation route, provenance, and local naming row.

Finally apply ¥autoref{thm:streamname-open-phase-budget-consumer-terminality}. Once the four faces and displayed budget rows agree, every accepted budget consumer determines the same terminal four-face route. The converse clause of the normal form and ledger exactness therefore accepts any packet exposing exactly those rows at the terminal classifier surface, and the cited exclusions leave no coordinate for quotient stream equality, host sequence equality, selected limits, ambient RealUp completeness, metric-completeness data, countable choice, or standard bridge rows.
¥end{proof}

¥begin{theorem}[StreamName open-phase no-fifth-object exhaustion]
¥label{thm:streamname-open-phase-no-fifth-object-exhaustion}
Every accepted Phase Real and Completion exit route in the current open phase is exhausted by the four L10 faces
$$
¥StreamNameUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows. There is no fifth object, aggregate verification token, quotient stream, selected limit, ambient completeness row, metric-completeness datum, countable-choice row, or standard bridge row hidden behind the terminal exit route.
¥end{theorem}
¥begin{proof}
First apply the four-face normal form of ¥autoref{thm:streamname-open-phase-four-face-normal-form}. It identifies accepted exit reads with the StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, and the displayed support rows.

Next use budget-consumer terminality from ¥autoref{thm:streamname-open-phase-budget-consumer-terminality}. Any accepted budget consumer determines the same terminal route once the four faces and budget rows agree, so a separate consumer token cannot add an object beyond the listed faces.

Apply ¥autoref{thm:streamname-open-phase-exit-route-completeness}. It supplies the converse direction: a packet exposing exactly the four faces and support rows is accepted by the terminal open-phase classifier surface.

Finally use the four-face ledger exactness of ¥autoref{thm:streamname-open-phase-four-face-ledger-exactness} and the four-face exit readback of ¥autoref{thm:streamname-open-phase-four-face-exit-readback}. They keep the tolerance ledger and readback rows inside the same displayed packet, leaving no route for a quotient stream, selected limit, ambient completeness theorem, metric-completeness datum, countable-choice row, standard bridge row, or hidden fifth object.
¥end{proof}

¥begin{theorem}[StreamName open-phase roadmap exit conjunction]
¥label{thm:streamname-open-phase-roadmap-exit-conjunction}
The current Phase Real and Completion paper-side boundary condition is the conjunction of the four local faces
$$
¥DyadicRatCoreUp,¥quad ¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
read componentwise through their own local closurestatus and formalstatus records and through the shared support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
This conjunction is sufficient only for the current paper-side boundary and audit-readiness route. Full phase exit is read objectwise from each face's own closurestatus and formalstatus records; no aggregate bridge or formalstatus token is created. It does not assert selected limits, quotient stream equality, ambient $¥RealUp$ completeness, metric completeness, countable choice, or standard bridge completion.
¥end{theorem}
¥begin{proof}
Start with ¥autoref{thm:streamname-open-phase-exit-route-completeness}. It states that an accepted Phase Real and Completion exit packet is exactly the terminal finite route through the StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, and the displayed support rows.

Next apply ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. This removes any hidden fifth object or aggregate token from the boundary, so the route can only be read as the four displayed faces with their $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support.

Align this route with the roadmap by ¥autoref{thm:streamname-real-completion-four-object-exit-route}. The four objects named there are the same DyadicRatCore, StreamName, RegSeqRat, and Real faces, so the open-phase boundary and the Real-completion roadmap boundary have the same visible coordinates.

Finally use ¥autoref{thm:real-l10-four-face-audit-clean-handoff} and ¥autoref{thm:real-l10-exit-facewise-audit-obstruction}. They require each face to contribute its own closurestatus and formalstatus record and prevent any support row or aggregate audit token from replacing a missing local face record. Therefore the componentwise four-face conjunction is sufficient only for the paper-side boundary and audit-readiness route. Full phase exit remains an objectwise read from the four local records, and the excluded selected-limit, quotient-equality, completeness, choice, metric, aggregate bridge, and aggregate formalstatus claims remain outside the theorem.
¥end{proof}

¥begin{theorem}[StreamName open-phase exit audit consolidation]
¥label{thm:streamname-open-phase-exit-audit-consolidation}
An accepted Phase Real and Completion audit packet for the current $¥StreamNameUp$ open-phase exit is valid exactly when it exposes exactly the four local faces
$$
¥DyadicRatCoreUp,¥quad ¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp
$$
with each of $¥DyadicRatCoreUp$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$ exposing its own current-roadmap local theory-closure record and a verification record at least as strong as the audit-clean threshold, read from that face's own closurestatus block, with $¥bridgeCheckedV$ read only as the local face bridge token where that face records it, together with the displayed support rows
$$
¥BHist,¥quad ¥hsame,¥quad ¥Cont,¥quad ¥Pkg,¥quad ¥NameCert.
$$
Equivalently, validity is the conjunction of those four objectwise threshold records and those finite support rows, and nothing else.

The audit packet excludes quotient stream equality, selected limits, ambient $¥RealUp$ completeness, metric completeness, countable choice, standard bridge completion, and any aggregate formalstatus or bridge token.
¥end{theorem}
¥begin{proof}
For sufficiency, apply ¥autoref{thm:streamname-open-phase-roadmap-exit-conjunction}. It identifies the paper-side boundary condition as the four local Phase Real and Completion faces read through their own local records, plus the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows.

Then apply ¥autoref{thm:real-l10-objectwise-exit-threshold-equivalence} as a threshold read. The Real-side criterion says those local records must meet the current objectwise threshold: each face supplies the required local theory-closure row and a local formalstatus row meeting or exceeding $¥auditCleanV$, read from its own closurestatus block. If a face records $¥bridgeCheckedV$, that token is read only as that face's local bridge record; it is not converted into an aggregate formalstatus or bridge token.

Use ¥autoref{thm:streamname-open-phase-exit-route-completeness} to read that thresholded visible packet as an accepted terminal finite route.

For necessity, apply ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. It says every accepted open-phase exit route is exhausted by the same four faces and displayed rows. The ledger exactness of ¥autoref{thm:streamname-open-phase-four-face-ledger-exactness} fixes the tolerance-ledger coordinate inside the finite packet, while the readback theorem ¥autoref{thm:streamname-open-phase-four-face-exit-readback} fixes every current exit read on exactly those rows.

Finally use ¥autoref{thm:real-l10-objectwise-exit-threshold-equivalence} and ¥autoref{thm:real-l10-exit-facewise-audit-obstruction}. Mere record presence is not enough: the local rows must satisfy the threshold, and no aggregate support row can compensate for a missing or sub-threshold face. Thus the necessary and sufficient audit criterion is exactly the four facewise threshold records with the displayed support rows, with each face keeping its own local formalstatus token and with no aggregate formalstatus, bridge token, quotient equality, selected limits, ambient completeness, metric completeness, countable choice, or standard bridge completion.
¥end{proof}

¥begin{theorem}[StreamName RegSeqRat--Real selector-budget normal form]
¥label{thm:streamname-regseqrat-real-selector-budget-normal-form}
Every accepted Phase Real and Completion exit read whose visible faces are
$$
¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RealUp
$$
factors through one selector-budget packet. The packet consists exactly of the finite request row, selected-window row, dyadic tolerance row, regularity handoff row, $¥RealUp$ seal row, support and provenance rows, and local $¥NameCert$ row.

The factorization is read through the same surfaces used by the sibling $¥RealUp$, $¥RegSeqRatUp$, $¥DyadicRatCoreUp$, and $¥CauchyModulusRefinementUp$ chapters, namely ¥autoref{ch:concrete-instances-real-namecert}, ¥autoref{ch:concrete-instances-regseqrat-namecert}, ¥autoref{ch:concrete-instances-dyadicratcore-namecert}, and ¥autoref{ch:concrete-instances-cauchy-modulus-refinement-namecert}. It excludes quotient streams, host equality, selected limits, ambient completeness, and any fifth object.
¥end{theorem}
¥begin{proof}
First pull the Real and RegSeqRat faces back to the same dyadic window. By ¥autoref{thm:streamname-real-regseqrat-dyadic-window-pullback}, the $¥RealUp$ seal and $¥RegSeqRatUp$ readback share the $¥DyadicRatCoreUp$ tolerance ledger through the finite $¥StreamNameUp$ window.

Next expose the selector-budget rows. The Real-window budget pullback of ¥autoref{thm:streamname-real-window-budget-pullback} identifies the finite request, selected window, dyadic readbacks, regular handoff, Real seal, componentwise transport, continuation route, provenance, and local naming rows as one packet rather than as separate completion data.

Now use ¥autoref{thm:streamname-open-phase-budget-consumer-terminality}. Agreement on the displayed budget rows determines the terminal four-face consumer route, so any Phase Real or Completion exit read with those visible faces factors through the same selector-budget surface.

Finally apply ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. Since the terminal exit route is exhausted by the four displayed faces and support rows, no quotient stream, host equality, selected limit, ambient completeness row, or fifth object remains as an additional factor.
¥end{proof}

¥begin{theorem}[StreamName selector-budget defect localization]
¥label{thm:streamname-selector-budget-defect-localization}
Let an accepted Phase Real and Completion exit read expose the visible faces
$$
¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RealUp.
$$
If this read fails to factor through the selector-budget packet of ¥autoref{thm:streamname-regseqrat-real-selector-budget-normal-form}, then the defect is witnessed by at least one displayed finite request row, selected-window row, dyadic tolerance row, regularity handoff row, $¥RealUp$ seal row, $¥BHist$ row, $¥hsame$ row, $¥Cont$ row, $¥Pkg$ row, or local $¥NameCert$ support row.

The defect cannot be witnessed by quotient stream equality, host equality, selected limits, ambient completeness, aggregate formalstatus, aggregate bridge rows, countable choice, or any fifth object.
¥end{theorem}
¥begin{proof}
Apply ¥autoref{thm:streamname-regseqrat-real-selector-budget-normal-form}. It identifies the only selector-budget packet available to an accepted exit read with the four displayed faces, so a failure of factorization must be a failure of one coordinate in that packet.

The packet coordinates are local. The dyadic-window pullback of ¥autoref{thm:streamname-real-regseqrat-dyadic-window-pullback} fixes the shared $¥DyadicRatCoreUp$ tolerance ledger for the $¥RegSeqRatUp$ readback and the $¥RealUp$ seal. The Real-window budget pullback of ¥autoref{thm:streamname-real-window-budget-pullback} identifies the finite request, selected-window, dyadic tolerance, regularity handoff, seal, support, provenance, and local naming rows as the displayed selector budget.

Now use ¥autoref{thm:streamname-open-phase-budget-consumer-terminality}. Every accepted consumer coordinate is determined by those displayed rows, including the $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and local $¥NameCert$ support rows. Hence a defect in the factorization has to appear on at least one of those finite rows.

Finally apply ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. Since the terminal route is exhausted by the four visible faces and their support rows, quotient stream equality, host equality, selected limits, ambient completeness, aggregate formalstatus, aggregate bridge rows, countable choice, and any fifth object are not admissible witnesses for the defect.
¥end{proof}

¥begin{theorem}[StreamName selector-budget defect face-status obstruction]
¥label{thm:streamname-selector-budget-defect-face-status-obstruction}
Let an accepted Phase Real and Completion exit read expose exactly the visible faces
$$
¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥DyadicRatCoreUp,¥quad ¥RealUp.
$$
If the read either fails to factor through the selector-budget packet of ¥autoref{thm:streamname-regseqrat-real-selector-budget-normal-form} or fails the audit-packet criterion of ¥autoref{thm:streamname-open-phase-exit-audit-consolidation}, then the obstruction is witnessed by at least one displayed finite request row, selected-window row, dyadic tolerance row, regularity handoff row, $¥RealUp$ seal row, $¥BHist$ row, $¥hsame$ row, $¥Cont$ row, $¥Pkg$ row, local $¥NameCert$ support row, or by one of the four objectwise local closurestatus and formalstatus records attached to $¥StreamNameUp$, $¥RegSeqRatUp$, $¥DyadicRatCoreUp$, and $¥RealUp$.

The obstruction cannot be repaired or witnessed by quotient stream equality, selected limits, ambient $¥RealUp$ completeness, metric completeness, countable choice, aggregate formalstatus, aggregate bridge rows, or standard bridge completion.
¥end{theorem}
¥begin{proof}
First consider failure of selector-budget factorization. By ¥autoref{thm:streamname-selector-budget-defect-localization}, every such failure is already localized on one of the finite selector rows or support rows displayed by the four-face packet. The excluded quotient, limit, completeness, choice, aggregate, and bridge coordinates do not occur in that packet.

Now consider failure of the audit-packet criterion. Apply ¥autoref{thm:streamname-open-phase-exit-audit-consolidation}. It reads audit validity as exactly the four objectwise local closurestatus and formalstatus records, together with the displayed support rows. Hence a failed audit packet is witnessed either by one of those local face-status records or by one of the finite support rows already named above.

Finally combine the two cases with ¥autoref{thm:streamname-open-phase-roadmap-exit-conjunction} and ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. The roadmap theorem keeps full phase exit objectwise over the four displayed faces, while no-fifth-object exhaustion removes every hidden route behind the terminal classifier surface. Thus aggregate formalstatus, aggregate bridge rows, standard bridge completion, quotient stream equality, selected limits, ambient $¥RealUp$ completeness, metric completeness, and countable choice cannot substitute for a missing finite row or a missing local face-status record.
¥end{proof}

¥begin{theorem}[StreamName open-phase face-status obstruction localization]
¥label{thm:streamname-open-phase-face-status-obstruction-localization}
Let a current Phase Real and Completion exit read expose exactly the four visible faces
$$
¥DyadicRatCoreUp,¥quad ¥StreamNameUp,¥quad ¥RegSeqRatUp,¥quad ¥RealUp.
$$
If the read fails the roadmap exit audit, then the failure is witnessed by one of those four local closurestatus, formalstatus, leantarget, or bridgestatus records, or by one of the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows.

No aggregate formalstatus, aggregate bridge row, selected limit, quotient stream equality, ambient $¥RealUp$ completeness, metric completeness, countable choice, or standard bridge row can substitute for the missing local witness.
¥end{theorem}
¥begin{proof}
First identify the audit surface. By ¥autoref{thm:streamname-open-phase-exit-audit-consolidation}, the StreamName-side audit criterion is exactly the four local Phase Real and Completion face records together with the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ support rows.

Next identify the roadmap boundary. Apply ¥autoref{thm:streamname-open-phase-roadmap-exit-conjunction}. It reads the current exit as the same four-face conjunction over $¥DyadicRatCoreUp$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$, so failure of the roadmap exit audit must occur on a row carried by that conjunction.

Now import the Real-side componentwise obstruction. The objectwise face-status exit of ¥autoref{thm:real-l10-objectwise-face-status-exit} fixes the $¥RealUp$ L10 boundary as the four named face records plus the same displayed support rows, and ¥autoref{thm:real-l10-exit-facewise-audit-obstruction} says an audit failure cannot be absorbed by an aggregate row when one of those local face records is missing or sub-threshold.

Finally apply ¥autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. Since the open-phase route has no hidden replacement coordinate beyond the four displayed faces and their support rows, selected limits, quotient stream equality, ambient completeness, metric completeness, countable choice, aggregate formalstatus, aggregate bridge rows, and standard bridge rows are not available substitutes. The failure is therefore localized to one of the four local status records or to one of the displayed support rows.
¥end{proof}
