\section{StreamName Open-Phase Dependency Lattice}
\label{sec:streamname-open-phase-dependency-lattice}

\begin{theorem}[StreamName RegSeqRat Real open-phase dependency lattice]
\label{thm:streamname-regseqrat-real-open-phase-dependency-lattice}
Every Phase Real and Completion consumer of an accepted finite $\StreamNameUp$ window whose route reaches the $\RegSeqRatUp$ readback surface of \autoref{ch:concrete-instances-regseqrat-namecert} and the $\RealUp$ seal surface of \autoref{ch:concrete-instances-real-namecert} factors through the ordered finite route
$$
\StreamNameUp\text{ window}\longrightarrow \RegSeqRatUp\text{ readback}\longrightarrow \DyadicRatCoreUp\text{ ledger}\longrightarrow \RealUp\text{ seal}.
$$
The $\DyadicRatCoreUp$ ledger is the observation ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. Along the route the only public coordinates available to the consumer are displayed $\BHist$ observations, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows attached to the four finite surfaces.

Thus the open-phase lattice exposes a finite BEDC route from StreamName windows into RegSeqRat readback, DyadicRatCore ledger data, and the Real seal. It exports no quotient stream, no host sequence equality, no selected limit, no ambient $\RealUp$ completeness row, no metric-completeness datum, and no standard bridge row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-open-phase-terminal-route}. It places the Phase Real and Completion consumer on the accepted terminal finite packet and names the StreamName window, the $\RegSeqRatUp$ readback, the $\DyadicRatCoreUp$ ledger, the $\RealUp$ seal row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next use \autoref{thm:streamname-open-phase-four-face-lock}. The terminal packet is read as the ordered four-face route from the StreamName window through RegSeqRat readback and the DyadicRatCore ledger into the Real seal. This removes any interpretation in which those faces are independent carrier routes.

Now invoke \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. The four faces occupy one finite pullback surface, so a consumer reaching the RegSeqRat and Real surfaces must pass through the same finite StreamName-to-RegSeqRat-to-DyadicRatCore-to-Real packet.

Finally apply \autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}. The consumer can project only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows on that pullback. Since those rows contain no coordinate for quotient streams, host sequence equality, selected limits, ambient Real completeness, metric-completeness data, or standard bridge rows, none of those objects is exported by the open-phase lattice.
\end{proof}

\begin{theorem}[StreamName open-phase face-order no shortcut]
\label{thm:streamname-open-phase-face-order-no-shortcut}
An accepted Phase Real and Completion consumer starting from a finite $\StreamNameUp$ window reaches the public $\RealUp$ seal if and only if its displayed support factors through the ordered four faces
$$
\StreamNameUp\text{ window}\longrightarrow \RegSeqRatUp\text{ readback}\longrightarrow \DyadicRatCoreUp\text{ ledger}\longrightarrow \RealUp\text{ seal}
$$
with the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows on that finite route. Any route omitting $\RegSeqRatUp$ or $\DyadicRatCoreUp$, swapping their public read order, or replacing a face by quotient stream equality, host sequence equality, a selected limit, ambient $\RealUp$ completeness, metric completeness, or a standard bridge row lies outside the accepted open-phase lattice.
\end{theorem}
\begin{proof}
For the forward direction, begin with \autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. It identifies every accepted consumer that reaches the public $\RealUp$ seal through the open phase with the displayed StreamName, RegSeqRat, DyadicRatCore, and Real faces, and it restricts the visible coordinates to the listed finite BEDC rows.

Next apply \autoref{thm:streamname-open-phase-terminal-route} and \autoref{thm:streamname-open-phase-four-face-lock}. The terminal route names the finite packet, while the lock reads that packet in the public order $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, then $\RealUp$. Thus the consumer support factors through the ordered four-face route and not through independent carrier faces.

For the reverse direction, use \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. A displayed support with those four faces and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows is one finite pullback packet, so its target row is precisely the public $\RealUp$ seal exposed by the open-phase route.

It remains to exclude shortcuts. Apply \autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}. The consumer projections of the pullback packet are exhausted by the four displayed faces and their shared BEDC coordinates. Omitting either middle face, permuting the RegSeqRat and DyadicRatCore public reads, or substituting quotient equality, host equality, selected limits, completeness data, or a standard bridge row would require a coordinate absent from that exhaustion list. Hence such a route is not an accepted open-phase lattice route.
\end{proof}
