\begin{theorem}[StreamName L10 sibling route]
\label{thm:streamname-orphan-l10-sibling-route}
The $\StreamNameUp$ public finite-window route is the sibling source consumed
by $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$. Every such sibling read
passes through finite $\BHist$ observations, componentwise $\hsame$ transport,
displayed $\Cont$ rows, $\Pkg$ provenance, and local $\NameCert$ rows before a
regularity, dyadic observation, or terminal Real seal surface is available.
\end{theorem}
\begin{proof}
Project the public finite-window route from
\autoref{ch:concrete-instances-streamname-namecert}. The route exposes the
finite StreamName window and its unary history observations as the common
source row.

The three sibling chapters consume that source in distinct ways. The
$\RegSeqRatUp$ chapter reads it as the regular-rational source schedule,
\autoref{ch:concrete-instances-dyadicratcore-namecert} reads it as the window
support for dyadic observations, and \autoref{ch:concrete-instances-real-namecert}
reads it as the terminal Real seal source.

Because each sibling read is routed through the displayed $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows, the StreamName route is a citeable L10
sibling dependency rather than a hidden host sequence or completed stream.
\end{proof}

\begin{theorem}[StreamName Cauchy window transducer source route]
\label{thm:streamname-cauchy-window-transducer-source-route}
The finite-window row exported by $\StreamNameUp$ is the source row $S$ consumed by every accepted $\CauchyWindowTransducerUp$ packet. The route passes through \autoref{ch:concrete-instances-cauchy-window-transducer-namecert} only as displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-orphan-l10-sibling-route}. It identifies the StreamName public finite-window route as the sibling source consumed by RegSeqRat, DyadicRatCore, and Real-facing rows before any terminal seal can be read.

Now inspect \autoref{def:cauchy-window-transducer-carrier}. The first analytic coordinate of a transducer packet is exactly the StreamName source row $S$, and every later row is routed through $D,W,R,E,L,H,C,P,N$.

Coordinate exhaustion gives the exclusion. Since the transducer carrier has no host sequence coordinate and no completed stream coordinate, the StreamName contribution to the packet is precisely the displayed finite-window row transported through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data.
\end{proof}
