\section{Public obligation surface}
\label{sec:streamname-public-obligation-surface}

\begin{definition}[StreamNameUp public reindexing obligation]
\label{def:streamname-public-reindexing-obligation}
The public reindexing obligation for $\StreamNameUp$ is the finite BEDC row
package that, for every certified unary observation reindexer and every
$\mathsf{ProbeBundle}$ window, transports the pointwise $\RatUp$ rows of the
public countable-name interface through the finite-window interface and
records the resulting observation rows in the same $\mathsf{BHist}$ ledger.
The obligation cites
\autoref{thm:streamname-public-countable-name-interface},
\autoref{thm:streamname-public-finite-window-interface},
\autoref{thm:streamname-finite-window-reindexing-stability}, and
\autoref{thm:streamname-finite-window-reindexing-composition}; it introduces
no completion, metric, or quotient row.
\end{definition}

\begin{theorem}[StreamNameUp public constant obligation]
\label{thm:streamname-public-constant-obligation}
Every public constant $\StreamNameUp$ packet is accepted by the countable-name
interface and by every finite-window interface obtained from certified unary
observations. Its visible rows are exactly the constant $\RatUp$ seed row, the
pointwise carrier/classifier rows, the empty-window boundary, and the finite
ledger entries selected by the observation bundle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-public-countable-name-interface}. It exports the
constant stream witness together with the pointwise $\RatUp$ carrier and
classifier rows over certified unary observations.

Next apply \autoref{thm:streamname-public-finite-window-interface}. A finite
window only restricts those pointwise rows to the observations named by the
bundle, while the empty-window boundary contributes the vacuous case.

Thus the public constant obligation is the same constant seed read through
each selected observation row. No regularity witness, metric datum, completion
endpoint, or quotient representative is present in the public packet.
\end{proof}

\begin{theorem}[StreamNameUp public transport obligation]
\label{thm:streamname-public-transport-obligation}
Let two certified $\StreamNameUp$ observation maps be related by displayed
$\hsame$ rows, and let the finite-window $\Cont$ routes and $\Pkg$ provenance
rows be transported componentwise. Then every public finite-window classifier
row for the first map transports to a public finite-window classifier row for
the second map over the same certified unary observations.
\end{theorem}
\begin{proof}
Use \autoref{thm:streamname-public-countable-name-interface} to read the
public carrier and classifier rows as pointwise $\RatUp$ rows over certified
unary observations. The supplied $\hsame$ rows transport those pointwise rows.

Then use \autoref{thm:streamname-public-finite-window-interface} to restrict
the transported pointwise rows to the selected $\mathsf{ProbeBundle}$ window.
The transported $\Cont$ and $\Pkg$ rows preserve the same finite provenance
route through the public interface.

The resulting packet is therefore a public finite-window classifier row for
the second map. The construction does not add a completion or regularity row;
it only repacks the transported public rows.
\end{proof}

\begin{theorem}[StreamNameUp public finite-ledger obligation]
\label{thm:streamname-public-ledger-obligation}
For every public $\StreamNameUp$ finite-window packet, the exported ledger is
exactly the finite family of certified unary observation rows selected by its
$\mathsf{ProbeBundle}$ together with the corresponding pointwise $\RatUp$
classifier rows. Reindexing, restriction, and composition do not expose any
row outside that finite ledger.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-public-finite-window-interface}. It
identifies the finite-window surface as the restriction of the public
countable-name interface to the observations carried by the bundle.

For reindexing, apply
\autoref{thm:streamname-finite-window-reindexing-stability}. The reindexed
window reads pointwise rows only at observations whose images are members of
the original bundle.

For composition, apply
\autoref{thm:streamname-finite-window-reindexing-composition}. The two-step
and one-step reindexing routes repack the same endpoint, classifier, $\hsame$,
and finite ledger rows over the target bundle. Hence no hidden observation
source is exported.
\end{proof}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_public\_ledger\_obligation}

\begin{theorem}[StreamNameUp public RealUp handoff obligation]
\label{thm:streamname-public-real-handoff-obligation}
The public $\StreamNameUp$ handoff to downstream $\RegSeqRat$ and $\RealUp$
consumers is the package consisting of the countable-name interface, the
finite-window interface, the public reindexing obligation of
\autoref{def:streamname-public-reindexing-obligation}, the constant-stream
obligation of \autoref{thm:streamname-public-constant-obligation}, the
transport obligation of \autoref{thm:streamname-public-transport-obligation},
and the finite-ledger obligation of
\autoref{thm:streamname-public-ledger-obligation}. The handoff supplies
certified unary observation rows and pointwise rational classifier rows only;
it does not supply $\RegSeqRat$ regularity, $\RealUp$ completeness, or a
standard bridge.
\end{theorem}
\begin{proof}
The countable-name and finite-window interfaces provide the public carrier,
classifier, pointwise rational rows, and bundle restriction rows. The
reindexing obligation records how these rows move through certified unary
observation maps.

The constant, transport, and finite-ledger obligations give the three public
consumer cases: constant names, $\hsame/\Cont$ transport, and finite-window
ledger readback. Each case cites only the public StreamNameUp rows already
listed above.

Downstream $\RegSeqRat$ and $\RealUp$ chapters may therefore consume a stable
stream-name observation surface, but any regular Cauchy condition, completion
witness, or standard bridge must be supplied in the downstream chapter rather
than by this handoff.
\end{proof}

\begin{theorem}[StreamNameUp finite-window schedule exhaustion]
\label{thm:streamname-finite-window-schedule-exhaustion}
Any downstream finite-window request whose rows consist of a public
$\StreamNameUp$ observation map, certified $\UnaryHistory$ indices, a
$\mathsf{ProbeBundle}$ schedule, pointwise $\RatUp$ endpoint rows, and
$\RegSeqRat$ or $\RealUp$ consumer provenance is exhausted by the public
finite-window interface of
\autoref{thm:streamname-public-finite-window-interface}, the public reindexing
obligation of \autoref{def:streamname-public-reindexing-obligation}, the
transport obligation of \autoref{thm:streamname-public-transport-obligation},
the finite ledger of \autoref{thm:streamname-public-ledger-obligation}, and the
handoff boundary of \autoref{thm:streamname-public-real-handoff-obligation}.
The request introduces no additional $\RegSeqRat$ regularity row, $\RealUp$
completion row, quotient representative, hidden limit selector, or observation
source beyond that union.
\end{theorem}
\begin{proof}
Read the carrier and classifier through
\autoref{thm:streamname-public-finite-window-interface}. The public observation
map and certified $\UnaryHistory$ indices determine the displayed pointwise
$\RatUp$ rows, while the $\mathsf{ProbeBundle}$ schedule restricts those rows
to the requested finite window.

Next apply \autoref{def:streamname-public-reindexing-obligation}. It repacks
the same scheduled rows after any certified unary reindexing, so the displayed
bundle is a restriction and reindexing of the public countable-name surface
rather than a separate request for stream data.

Use \autoref{thm:streamname-public-transport-obligation} for the pointwise
rational endpoint rows. The supplied $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows
transport the endpoint classifiers componentwise and preserve the same
finite-window provenance.

Finally combine \autoref{thm:streamname-public-ledger-obligation} with
\autoref{thm:streamname-public-real-handoff-obligation}. The ledger identifies
all exposed rows as scheduled public observation rows and pointwise rational
classifiers, and the handoff theorem states that downstream $\RegSeqRat$ and
$\RealUp$ consumers must supply their own regularity, completion, quotient, and
limit-selection data. Hence the finite-window request is exhausted by the
listed public StreamNameUp obligations.
\end{proof}

\begin{theorem}[StreamNameUp RegSeqRat denominator-source exhaustion]
\label{thm:streamname-regseqrat-denominator-source-exhaustion}
Let a downstream $\RegSeqRat$ finite-window consumer receive as input a public
$\StreamNameUp$ finite-window request together with dyadic denominator rows.
Then the consumer reads exactly the selected $\mathsf{RatHistoryClassifier}$
rows, certified $\UnaryHistory$ observation rows, finite
$\mathsf{ProbeBundle}$ ledger, $\mathsf{InBundle}$ membership rows, displayed
$\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the
$\DyadicRatCoreUp$ denominator-ledger rows already exported by the dyadic
real-phase source boundary. It reads no $\RegSeqRat$ regularity witness, seal
classifier, completion datum, quotient representative, hidden limit selector,
or host index equality.
\end{theorem}
\begin{proof}
Start with the public real handoff of
\autoref{thm:streamname-public-real-handoff-obligation}. It exposes the
countable-name and finite-window StreamNameUp rows, the certified unary
observation surface, and the public pointwise rational classifier rows.

Next use \autoref{thm:streamname-finite-window-schedule-exhaustion}. The
finite request is therefore exhausted by the displayed observation indices,
probe bundle, bundle-membership rows, rational endpoint rows, $\hsame$
comparisons, continuation routes, and package provenance.

The RegSeqRat-facing handoff of
\autoref{thm:streamname-real-regseq-finite-window-handoff} identifies the same
finite rows as the rows consumed by the downstream regular-sequence interface.
The denominator side is supplied separately by
\autoref{thm:dyadicratcore-real-phase-source-coverage}, which contributes only
the dyadic denominator ledger exported by the real-phase source boundary.

Combining these two source boundaries gives the displayed row inventory. None
of the cited boundaries exports a regularity witness, seal classifier,
completion datum, quotient representative, hidden limit selector, or host
index equality, so no such datum can be read by the finite-window consumer.
\end{proof}

\begin{theorem}[StreamNameUp RegSeqRat window union exhaustion]
\label{thm:streamname-regseqrat-window-union-exhaustion}
Let two downstream finite-window requests over a common public
$\StreamNameUp$ observation map be displayed by probe bundles $B_1$ and
$B_2$. Suppose each request is exhausted by
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. Then the
combined request over the displayed bundle union is exhausted by the public
StreamName finite-window interface, the two displayed
$\mathsf{InBundle}$ membership families for $B_1$ and $B_2$, the pointwise
$\RatUp$ classifier rows, the dyadic denominator ledger rows, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ provenance. The union request exports no
$\RegSeqRat$ regularity witness, $\RealUp$ completion row, quotient
representative, hidden limit selector, or host index equality.
\end{theorem}
\begin{proof}
Start from the common public classifier supplied by
\autoref{thm:streamname-public-finite-window-interface}. It fixes the
observation map, the certified $\UnaryHistory$ observation rows, and the
pointwise $\RatUp$ classifier rows before either downstream finite request is
chosen.

Apply \autoref{thm:streamname-finite-window-schedule-exhaustion} separately
to $B_1$ and to $B_2$. This gives two finite schedules with their displayed
$\mathsf{InBundle}$ membership families, $\hsame$ comparisons, $\Cont$
routes, and $\mathsf{Pkg}$ provenance, all over the same public StreamName
observation surface.

Next use \autoref{thm:streamname-regseqrat-denominator-source-exhaustion} for
each scheduled request. The first request contributes only its displayed
observation rows and dyadic denominator ledger rows, and the second request
contributes the same kind of displayed rows over its own membership family.

It remains to repack the two finite ledgers. For an observation in the
displayed bundle union, case on whether the membership row comes from $B_1$
or from $B_2$. In the first case read the row from the first exhausted
request; in the second case read it from the second exhausted request. If a
row is displayed by both bundles, the common public classifier and the
displayed $\hsame$ rows identify the two readbacks as the same public
StreamName observation row.

Thus every row in the combined finite request is one of the displayed public
observation, membership, rational-classifier, denominator-ledger,
continuation, or provenance rows already listed. Since neither component
exhaustion theorem exports regularity, completion, quotient, limit-selection,
or host index equality data, the bundle-union request exports none of those
rows.
\end{proof}

\begin{theorem}[StreamName finite-window terminal schedule idempotence]
\label{thm:streamname-finite-window-terminal-schedule-idempotence}
Let a public $\StreamNameUp$ observation map be read over certified
$\UnaryHistory$ indices, and let a finite $\mathsf{ProbeBundle}$ schedule
$B$ display the downstream source request. Suppose a terminal downstream
$\RegSeqRat$ or $\RealUp$ consumer has source rows exactly the scheduled
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the displayed
$\mathsf{InBundle}$ membership rows for $B$, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the dyadic denominator rows, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ provenance. Then applying the same schedule
boundary a second time exposes the same finite source projection.

The second pass supplies no additional regularity witness, completion datum,
quotient representative, hidden limit selector, or host index row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-finite-window-schedule-exhaustion} to the
first pass through $B$. This identifies the public observation packet as the
displayed finite schedule: certified $\UnaryHistory$ indices, the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, membership in $B$,
pointwise rational classifier rows, $\hsame$, $\Cont$, and $\mathsf{Pkg}$
provenance.

Attach the denominator side by
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. The
terminal consumer may therefore read the dyadic denominator boundary only as
part of the displayed finite source ledger, not as an independent
$\RegSeqRat$ regularity or $\RealUp$ completion row.

Now use \autoref{thm:streamname-regseqrat-window-union-exhaustion} with
$B_1=B_2=B$. The displayed bundle union is again $B$, so the second boundary
request reads the same membership family, the same rational classifier rows,
the same denominator rows, and the same continuation and provenance rows as
the first request.

Finally apply \autoref{thm:streamname-public-ledger-obligation} and
\autoref{thm:streamname-public-real-handoff-obligation}. These obligations
exclude non-displayed rows from the public StreamName handoff, so a repeated
boundary cannot create a fresh regularity witness, completion datum, quotient
representative, hidden limit selector, or host index row. The terminal source
projection is therefore idempotent under the repeated finite schedule.
\end{proof}

\begin{theorem}[StreamNameUp pointwise hsame reindexing stability]
\label{thm:streamname-pointwise-hsame-reindexing-stability}
Let a public $\StreamNameUp$ observation map be read through certified
$\UnaryHistory$ reindexers, and let a finite $\mathsf{ProbeBundle}$ window
$B$ display the source request. Suppose the source and target observation
rows are related pointwise by the displayed $\hsame$ relation, and suppose the
reindexing routes are carried by the same $\Cont$ and $\Pkg$ provenance rows.
Then the public finite-window classifier packet transports to the reindexed
window.

The transported packet exposes only certified unary observation rows,
pointwise $\RatUp$ classifier rows, $\mathsf{InBundle}$ membership,
$\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance. It supplies no
$\RegSeqRat$ regularity, $\RealUp$ completion, quotient representative,
hidden limit selector, or host index equality.
\end{theorem}
\begin{proof}
Start from the public reindexing obligation of
\autoref{def:streamname-public-reindexing-obligation}. It identifies the
source and target observation rows through certified $\UnaryHistory$
reindexers and keeps the route inside the displayed $\Cont$ and $\Pkg$
provenance.

Apply \autoref{thm:streamname-public-transport-obligation} to the pointwise
$\hsame$ comparisons. The rational classifier row attached to each source
observation is carried to the corresponding target observation without
creating a host index equality or a quotient representative.

Project the finite rows by
\autoref{thm:streamname-finite-window-schedule-exhaustion}. The reindexed
window therefore has exactly the certified observation rows,
$\mathsf{InBundle}$ membership rows, pointwise rational rows, continuation
routes, and package provenance listed by the public window schedule.

Finally use \autoref{thm:streamname-public-ledger-obligation} and the union
exhaustion of \autoref{thm:streamname-regseqrat-window-union-exhaustion} to
rule out extra consumer rows. Since those ledgers contain no regularity,
completion, quotient, limit-selection, or host-equality coordinate, the
transported finite-window packet exposes none of that data.
\end{proof}

\begin{theorem}[StreamNameUp public reindexing composition]
\label{thm:streamname-public-reindexing-composition}
Let $r$ and $s$ be certified $\UnaryHistory$ reindexers displayed over finite
$\mathsf{ProbeBundle}$ windows for a public $\StreamNameUp$ observation map.
Suppose the $r$ leg transports every displayed public observation row by
pointwise $\hsame$ through its recorded $\Cont$ route and $\Pkg$ provenance,
and suppose the $s$ leg does the same for the reindexed window. Then the
composite reindexer transports the same finite-window classifier packet.

The composite packet consists only of $\UnaryHistory$ observation rows,
$\mathsf{InBundle}$ membership, pointwise $\RatUp$ classifier rows, $\hsame$
comparisons, composed $\Cont$ provenance, and the displayed $\Pkg$ rows. It
does not export $\RegSeqRat$ regularity, $\RealUp$ completion, quotient
representatives, selected limits, or host index equality.
\end{theorem}
\begin{proof}
Apply the public reindexing obligation of
\autoref{def:streamname-public-reindexing-obligation} to the $r$ leg and then
to the $s$ leg. Each application reads only certified $\UnaryHistory$
observation rows, displayed membership, pointwise rational classifier rows,
and the recorded $\Cont$ and $\Pkg$ provenance for that leg.

Use \autoref{thm:streamname-public-transport-obligation} on the pointwise
$\hsame$ rows supplied by both legs. The first application transports the
source classifier row to the intermediate window, and the second transports
the intermediate row to the target window. Composing the two displayed
$\Cont$ routes gives the route used by the composite packet, while the
$\Pkg$ rows remain exactly the provenance rows displayed by the two legs.

Project the finite target window by
\autoref{thm:streamname-finite-window-schedule-exhaustion}. The projection
lists precisely the $\UnaryHistory$ observation rows, $\mathsf{InBundle}$
membership, pointwise $\RatUp$ classifier rows, $\hsame$ comparisons,
continuation routes, and package provenance exposed by the composite
finite-window schedule.

Finally combine \autoref{thm:streamname-public-ledger-obligation} with the
window-union exhaustion of
\autoref{thm:streamname-regseqrat-window-union-exhaustion}. Any row seen by a
consumer of the composite window must already appear in one of the two
displayed leg ledgers or in their finite union. Since those ledgers carry no
regularity, completion, quotient, selected-limit, or host-index coordinate,
the composite public packet exports none of those objects.
\end{proof}

\begin{theorem}[StreamNameUp public RegSeqRat reindexing cover lock]
\label{thm:streamname-public-regseqrat-reindexing-cover-lock}
Let a finite cover of public $\StreamNameUp$ windows feed downstream
$\RegSeqRatUp$ or finite $\RealUp$ consumers. Suppose each cover member is
carried by certified unary reindexing and by displayed $\hsame$, $\Cont$, and
$\Pkg$ transport. Then the reindexed cover preserves the same union and overlap
inventories: unary observation rows, $\mathsf{InBundle}$ membership, pointwise
$\RatUp$ classifier rows, $\DyadicRatCoreUp$ denominator rows, and provenance.

The cover lock exports no $\RegSeqRatUp$ regularity witness, $\RealUp$
completion row, quotient representative, hidden limit selector, or host index
equality.
\end{theorem}
\begin{proof}
Begin with the reindexing composition theorem
\autoref{thm:streamname-public-reindexing-composition}. It shows that certified
unary reindexing carries exactly the displayed public observation rows,
membership rows, pointwise rational classifier rows, $\hsame$ comparisons,
continuation routes, and package provenance.

Use \autoref{thm:streamname-regseqrat-window-union-exhaustion} to read the
finite cover as one public union inventory. On intersections of cover members,
apply \autoref{thm:streamname-regseqrat-window-intersection-exhaustion}; the
overlap rows are the common displayed StreamName observations, membership
rows, pointwise rational rows, denominator rows, and provenance.

Finally apply
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion} to each
downstream read. It accounts for the dyadic denominator rows consumed by
regular-rational and finite real-facing windows, while the preceding union and
intersection steps show that reindexing has added no regularity, completion,
quotient, hidden selector, or host-equality coordinate.
\end{proof}

\begin{theorem}[StreamNameUp RegSeqRat window intersection exhaustion]
\label{thm:streamname-regseqrat-window-intersection-exhaustion}
Let two downstream finite-window requests over a common public
$\StreamNameUp$ observation map be exhausted by
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. Suppose the
two requests both restrict to a certified common sub-bundle $K$. Then the
common restricted request over $K$ is exhausted by the public StreamName
finite-window interface, the displayed $\mathsf{InBundle}(-,K)$ membership
rows, the pointwise $\RatUp$ classifier rows, the dyadic denominator ledger
rows, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance. The common restricted
request exports no $\RegSeqRat$ regularity witness, $\RealUp$ completion row,
quotient representative, hidden limit selector, or host index equality.
\end{theorem}
\begin{proof}
Start with the two displayed downstream finite-window requests and restrict
each one to the certified common sub-bundle $K$. By
\autoref{thm:streamname-finite-window-schedule-exhaustion}, each restriction
has only the public observation rows, $\mathsf{InBundle}(-,K)$ membership
rows, pointwise rational classifier rows, $\hsame$ comparisons, $\Cont$
routes, and $\mathsf{Pkg}$ provenance inherited from the common
$\StreamNameUp$ observation surface.

Apply \autoref{thm:streamname-regseqrat-denominator-source-exhaustion} to
each restricted side. The two reads may add the displayed dyadic denominator
ledger rows, but they add no regularity witness, completion row, quotient
representative, hidden limit selector, or host index equality.

It remains to identify the common row inventory. For an observation in $K$,
membership is witnessed on both restricted requests by the displayed
$\mathsf{InBundle}(-,K)$ row. Reading the row from either side gives the same
public StreamName observation, because the observation map is common and the
displayed $\hsame$ rows compare the same pointwise $\RatUp$ classifier data.

Thus the common restricted request contains only the public finite-window
rows, common membership rows, pointwise rational rows, denominator-ledger
rows, continuation rows, and provenance rows listed in the statement. Since
the cited component exhaustions export none of the excluded downstream data,
the common subwindow exports none of it.
\end{proof}

\begin{theorem}[StreamName pointwise classifier finite-window separation]
\label{thm:streamname-pointwise-classifier-finite-window-separation}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be certified rational StreamName
observation maps, and let their public $\NameCert$ rows display the
$\mathsf{BHist}$ carrier, $\hsame$ transport, $\Cont$ routes, and
$\mathsf{Pkg}$ provenance required by the finite-window interface. If the
pointwise StreamName classifier for $s$ and $t$ does not hold, then there is a
certified unary index $n$, a finite $\mathsf{ProbeBundle}$ window $K$ carrying
$n$, and a finite-window $\mathsf{Pkg}$ row over $K$ such that the selected
endpoint packages $s(n)$ and $t(n)$ are not identified by the downstream
$\RegSeqRat/\RealUp$ seal classifier read from that row.

Conversely, if a certified finite-window package over some $K$ carries a
certified unary index $n$ and displays endpoint packages $s(n)$ and $t(n)$
which the $\RegSeqRat/\RealUp$ seal classifier does not identify, then the
pointwise StreamName classifier for $s$ and $t$ fails. The separating package
uses only the displayed $\mathsf{BHist}$ observations, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, $\mathsf{InBundle}$, pointwise $\RatUp$ rows, and $\NameCert$
provenance.
\end{theorem}
\begin{proof}
For the forward direction, restrict the failed pointwise classifier to a
certified unary observation at which its displayed endpoint row is not
identified. The finite-window interface supplies a singleton
$\mathsf{ProbeBundle}$ carrying that observation, and
\autoref{thm:streamname-finite-window-schedule-exhaustion} identifies the
resulting packet as a public $\mathsf{BHist}$ window with the corresponding
$\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows.

Next pass the singleton packet through the common-window machinery. Apply
\autoref{thm:streamname-finite-window-common-refinement-export} to regard the
singleton as a certified subwindow of any displayed comparison window, and use
\autoref{thm:streamname-window-common-refinement-readback} to read back the
selected endpoint packages $s(n)$ and $t(n)$ from the same finite
$\NameCert$ provenance row.

Finally use
\autoref{thm:streamname-regseqrat-window-intersection-exhaustion} together
with \autoref{thm:streamname-real-regseq-finite-window-handoff}. The handoff
theorem says the downstream $\RegSeqRat/\RealUp$ read sees exactly the selected
StreamName endpoint packages and the displayed denominator ledger; the
intersection exhaustion prevents any hidden regularity, completion, quotient,
or host-index row from identifying endpoints that the selected package
separates.

For the reverse direction, start with the separating certified package over
$K$. The selected $\mathsf{InBundle}(n,K)$ row and the
$\mathsf{UnaryHistory}$ certificate restrict the public StreamName classifier
to the endpoint comparison at $n$.

If the pointwise classifier for $s$ and $t$ held, the finite-window
restriction theorem would transport that pointwise row into the same
$\mathsf{Pkg}$ packet, and the RegSeqRat/RealUp handoff would read an
identified seal endpoint there. This contradicts the displayed separating seal
row, so the pointwise classifier fails.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp observation coverage]
\label{thm:streamname-regseqrat-realup-observation-coverage}
Every finite-window handoff from public $\StreamNameUp$ to a downstream
$\RegSeqRat$ consumer or finite-window $\RealUp$ consumer is covered exactly by
certified $\UnaryHistory$ observation rows, $\mathsf{ProbeBundle}$ scheduling
rows, $\mathsf{InBundle}$ membership rows, pointwise $\RatUp$ classifier rows,
displayed $\hsame$ comparisons, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
the $\DyadicRatCoreUp$ denominator ledger exposed at the real-phase source
boundary. The handoff exports no $\RegSeqRat$ regularity witness, $\RealUp$
completion row, quotient representative, hidden limit selector, or host index
equality.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-public-real-handoff-obligation}. It fixes the
public observation surface for downstream $\RegSeqRat$ and finite-window
$\RealUp$ consumers, and it restricts the handoff to displayed StreamNameUp
rows rather than to host streams.

Apply \autoref{thm:streamname-finite-window-schedule-exhaustion}. The finite
request is then exhausted by the certified $\UnaryHistory$ observation rows,
the $\mathsf{ProbeBundle}$ schedule, $\mathsf{InBundle}$ membership, pointwise
$\RatUp$ classifier rows, displayed $\hsame$ comparisons, continuation routes,
and package provenance.

For a $\RegSeqRat$ consumer, use
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. It identifies
the same public observation rows and adds only the dyadic denominator ledger
needed by the regular-sequence interface.

Finally, \autoref{thm:dyadicratcore-real-phase-source-coverage} supplies the
source boundary for that denominator ledger. Thus the public observation rows,
the dyadic denominator rows, and the downstream seal boundary form one finite
BEDC source inventory. The exclusion clauses follow because none of the four
cited boundaries exports regularity witnesses, completion rows, quotient
representatives, hidden limit selectors, or host index equality.
\end{proof}

\begin{theorem}[StreamName public denominator positive source fit]
\label{thm:streamname-public-denominator-positive-source-fit}
Every finite-window public $\StreamNameUp$ handoff accepted by
\autoref{thm:streamname-regseqrat-realup-observation-coverage} has its selected
denominator source read from the displayed $\DyadicRatCoreUp$ denominator
ledger. The selected denominator rows are positive unary denominator rows in
the $\RatUp$ classifier sense, are stable under the displayed $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ transport, and are exactly the source consumed by
the downstream $\RegSeqRat$ or finite-window $\RealUp$ read. The handoff
introduces no regularity witness, completion datum, quotient representative,
hidden limit selector, or host index equality.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:streamname-regseqrat-realup-observation-coverage}. It confines the
finite-window handoff to certified $\UnaryHistory$ observation rows, the
finite $\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, pointwise $\RatUp$
classifier rows, displayed transport rows, provenance rows, and the
$\DyadicRatCoreUp$ denominator ledger.

Next apply
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. The
downstream regular-sequence read can therefore choose its denominator source
only from the same displayed denominator ledger named by the public handoff.

Use \autoref{thm:dyadicratcore-real-phase-source-coverage} for the dyadic
source row. Its denominator boundary supplies positive unary denominator rows
in the $\RatUp$ classifier sense, and the displayed $\hsame$, $\Cont$, and
$\mathsf{Pkg}$ rows transport those rows without changing the finite source
inventory.

Repack the handoff with that denominator row as the consumed source. Since all
cited boundaries are finite ledger statements and none exports regularity,
completion, quotient, limit-selection, or host equality data, the selected
positive denominator source is exactly the visible source available downstream.
\end{proof}

\begin{theorem}[StreamName RegSeqRat public overlap lock]
\label{thm:streamname-regseqrat-public-overlap-lock}
Let two public $\StreamNameUp$ finite-window handoffs feed downstream
$\RegSeqRat$ consumers or finite-window $\RealUp$ consumers over the same
observation map. If an observation row lies in the certified overlap of the two
displayed $\mathsf{ProbeBundle}$ windows, then both consumers read the same
public $\StreamNameUp$ observation row, the same pointwise $\RatUp$ classifier
row, the same dyadic denominator ledger row, and the same displayed $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ provenance.

The overlap lock exposes no $\RegSeqRat$ regularity witness, completion row,
quotient representative, hidden limit selector, or host index equality.
\end{theorem}
\begin{proof}
First restrict both handoff requests to the certified common window. Apply
\autoref{thm:streamname-regseqrat-window-intersection-exhaustion}; each
consumer read over the overlap is exhausted by the same public StreamName
observation row, the same $\mathsf{InBundle}$ membership row, and the same
pointwise classifier surface.

Next compare the two finite-window ledgers inside the combined display. Apply
\autoref{thm:streamname-regseqrat-window-union-exhaustion}. The union ledger
has no extra consumer coordinate beyond the rows already exposed by the two
windows, so an overlap row is read through one shared public bundle inventory.

Now identify the denominator source. Use
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion} together with
\autoref{thm:streamname-public-denominator-positive-source-fit}. The downstream
denominator row is the displayed positive $\DyadicRatCoreUp$ source row, and
the same $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows carry it through both
handoffs.

Finally apply
\autoref{thm:streamname-regseqrat-realup-observation-coverage}. Its exclusion
clauses rule out regularity witnesses, completion rows, quotient
representatives, hidden limit selectors, and host index equality. Hence the
overlap determines only the visible public rows listed above.
\end{proof}

\begin{theorem}[StreamNameUp RegSeqRat cover-refinement exhaustion]
\label{thm:streamname-regseqrat-cover-refinement-exhaustion}
Let $\mathcal{U}=\{B_i\}_{i\in I}$ be a finite cover family of public
$\StreamNameUp$ windows over a common observation map. Suppose every $B_i$ is
exhausted by
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}, and let
$\mathcal{R}$ be a certified common refinement cover read by a downstream
$\RegSeqRatUp$ consumer or finite-window $\RealUp$ consumer. Then the
refinement read is exhausted by the public StreamName finite-window interface,
the displayed $\mathsf{InBundle}$ membership rows for the cover members and
for $\mathcal{R}$, pointwise $\RatUp$ classifier rows, the
$\DyadicRatCoreUp$ denominator ledger, $\hsame$, $\Cont$, and $\mathsf{Pkg}$
provenance. The refinement read exports no $\RegSeqRatUp$ regularity witness,
$\RealUp$ completion row, quotient representative, hidden limit selector, or
host index equality.
\end{theorem}
\begin{proof}
Begin with the public finite-window interface. It fixes the common
$\StreamNameUp$ observation map, the visible observation histories, the
pointwise $\RatUp$ classifier rows, and the public transport and provenance
rows before the downstream cover refinement is read.

For each cover member $B_i$, apply
\autoref{thm:streamname-regseqrat-denominator-source-exhaustion}. The member
read contributes only its displayed $\mathsf{InBundle}(-,B_i)$ rows, public
observation rows, pointwise rational classifier rows, dyadic denominator
ledger rows, $\hsame$ comparisons, $\Cont$ routes, and $\mathsf{Pkg}$
provenance.

Next pass through the finite cover by the union and intersection exhaustion
theorems. Use
\autoref{thm:streamname-regseqrat-window-union-exhaustion} to combine the
member inventories, and use
\autoref{thm:streamname-regseqrat-window-intersection-exhaustion} on overlap
rows so that a refinement point covered by more than one $B_i$ has one common
public row inventory.

It remains to repack the certified common refinement. Case on the displayed
$\mathsf{InBundle}$ membership row for a refinement element of
$\mathcal{R}$. The certification names a cover member $B_i$ containing that
element, so the row is read from the exhausted inventory of $B_i$; on overlaps,
the intersection exhaustion identifies the alternative reads by the common
public classifier and the displayed $\hsame$ rows.

Thus every row consumed by the downstream $\RegSeqRatUp$ or finite-window
$\RealUp$ refinement read is one of the displayed public StreamName window
rows, refinement-membership rows, pointwise rational rows, denominator-ledger
rows, continuation rows, or provenance rows. Since the member, union, and
intersection exhaustions export none of the excluded regularity, completion,
quotient, limit-selection, or host-equality data, the common refinement cover
exports none of those rows.
\end{proof}

\begin{theorem}[StreamNameUp RegSeqRat cover-refinement transitivity]
\label{thm:streamname-regseqrat-cover-refinement-transitivity}
Let $\mathcal{U}=\{B_i\}_{i\in I}$ be a finite cover family of public
$\StreamNameUp$ windows over a common observation map, and suppose the cover is
exhausted by
\autoref{thm:streamname-regseqrat-cover-refinement-exhaustion}. Let
$\mathcal{R}$ be a certified refinement cover whose downstream
$\RegSeqRatUp$ or finite-window $\RealUp$ read is exhausted by the same public
rows, and let $\mathcal{S}$ be a second certified refinement cover refining
$\mathcal{R}$. Then every downstream $\RegSeqRatUp$ or finite-window
$\RealUp$ read over $\mathcal{S}$ is exhausted by the original public
StreamName finite-window interface, the displayed memberships
$$
\begin{gathered}
\mathsf{InBundle}(-,B_i),\\
\mathsf{InBundle}(-,\mathcal{R}),\\
\mathsf{InBundle}(-,\mathcal{S}),
\end{gathered}
$$
the pointwise $\RatUp$ classifier rows, the $\DyadicRatCoreUp$ denominator
ledger, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ provenance.

This transitive refinement read exports no $\RegSeqRatUp$ regularity witness,
no $\RealUp$ completion row, no quotient representative, no hidden limit
selector, and no host index equality.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-cover-refinement-exhaustion} to the
$\mathcal{R}$ cover. The result identifies every read over $\mathcal{R}$ with
the public $\StreamNameUp$ finite-window interface, the member
$\mathsf{InBundle}(-,B_i)$ rows, the refinement-membership rows for
$\mathcal{R}$, the pointwise classifier rows, and the displayed denominator,
transport, continuation, and provenance ledger.

Next compose the membership route for the second refinement. Use
\autoref{thm:streamname-finite-window-refinement-transitivity} to send each
$\mathcal{S}$ row through its certified $\mathcal{R}$ row and then through the
containing public window $B_i$. This gives a single public route
$$
\mathcal{S}\to\mathcal{R}\to\mathcal{U}
$$
for the displayed $\mathsf{InBundle}$ evidence at all three cover levels.

Now transport the endpoint rows along that route. Apply
\autoref{thm:streamname-cover-refinement-transport-closure}. The transported
endpoint rows remain the same public observation rows, pointwise $\RatUp$
classifier rows, $\DyadicRatCoreUp$ denominator rows, $\hsame$ comparisons,
$\Cont$ continuations, and $\mathsf{Pkg}$ provenance rows already named by the
first refinement read.

Finally compare overlapping reads in the composed cover. Use
\autoref{thm:streamname-regseqrat-window-union-exhaustion} to combine the
visible inventories and
\autoref{thm:streamname-regseqrat-window-intersection-exhaustion} to identify
rows that enter through two cover members. These exhaustion results preserve
the same exclusion clauses as the first refinement, so the downstream
$\mathcal{S}$ read contains no regularity witness, completion row, quotient
representative, hidden limit selector, or host index equality.
\end{proof}
