\section{StreamName Real-Completion Gateway Package}
\label{sec:streamname-real-completion-gateway-package}

\begin{definition}[StreamName Real-completion gateway carrier]
\label{def:streamname-real-completion-gateway-carrier}
A $\StreamNameUp$ Real-completion gateway packet is a finite $\BHist$ packet
$$
G=(S,D,R,E,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ finite-window row read by the open phase;
\item $D$ is the $\DyadicRatCoreUp$ tolerance-ledger row anchored to the same finite window;
\item $R$ is the $\RegSeqRatUp$ readback row produced from that anchored window;
\item $E$ is the $\RealUp$ seal row reachable only after the displayed readback;
\item $B$ records the displayed $\BHist$ observations on $S,D,R,E$;
\item $H$ records componentwise $\hsame$ transports for the window, ledger, readback, seal, route, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ routes from $S$ to $D$, from $S,D$ to $R$, and from $R$ to $E$;
\item $P$ records $\Pkg$ provenance over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ records the local $\NameCert_{\StreamNameUp}$ rows for the four faces and their displayed support.
\end{enumerate}
The packet is a gateway for the finite Real-completion route. It contains no coordinate for quotient stream equality, host sequence equality, a selected limit, ambient $\RealUp$ completeness, metric-completeness data, or a standard bridge row.
\end{definition}

\begin{theorem}[StreamName Real-completion gateway obligations]
\label{thm:streamname-real-completion-gateway-obligations}
For the carrier of \autoref{def:streamname-real-completion-gateway-carrier}, the local $\NameCert_{\StreamNameUp}$ obligations are exactly carrier admission for
$$
G=(S,D,R,E,B,H,C,P,N),
$$
StreamName finite-window exposure through $S$, DyadicRatCore tolerance-ledger exposure through $D$, RegSeqRat readback exposure through $R$, RealUp seal exposure through $E$, displayed $\BHist$ observation through $B$, componentwise $\hsame$ transport through $H$, displayed route replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-open-phase-exit-boundary}. It identifies every Phase Real and Completion consumer with the finite StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, and the displayed observation, transport, route, provenance, and local naming rows.

Next apply \autoref{thm:streamname-real-completion-exit-certificate}. The certificate repacks the same exit boundary as a four-face read and names exactly the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows used by the gateway packet.

Finally use \autoref{thm:streamname-dyadicratcore-window-anchor}. The tolerance ledger is pinned to the StreamName finite window before the RegSeqRat readback or the RealUp seal can be consumed. Therefore the listed rows exhaust the local NameCert obligations for the gateway carrier.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway non-escape]
\label{thm:streamname-real-completion-gateway-nonescape}
No accepted $\StreamNameUp$ Real-completion gateway packet exports quotient stream equality, host sequence equality, a selected limit, ambient $\RealUp$ completeness, metric-completeness data, countable-choice selection, or a standard bridge row. Every accepted gateway read factors through
$$
S,D,R,E,B,H,C,P,N
$$
as displayed in \autoref{def:streamname-real-completion-gateway-carrier}.
\end{theorem}
\begin{proof}
Begin with the gateway obligation theorem. It says that every public read of the packet is one of $S,D,R,E,B,H,C,P,N$ and that the structural rows only transport, replay, package, and name that displayed inventory.

Use \autoref{thm:streamname-open-phase-exit-boundary} and \autoref{thm:streamname-real-completion-exit-certificate}. Both exclude quotient streams, host sequence equality, selected limits, ambient Real completeness, metric-completeness data, and standard bridge rows from the same four-face boundary.

It remains to exclude a bypass through the dyadic ledger. Apply \autoref{thm:streamname-dyadicratcore-window-anchor}: the ledger is anchored to the StreamName finite window before RegSeqRat or Real consumers can inspect it. Thus the gateway has no second route through which any excluded object can enter.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway terminality]
\label{thm:streamname-real-completion-gateway-terminality}
Let two accepted $\StreamNameUp$ Real-completion gateway reads expose the same StreamName finite window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, displayed $\BHist$ observations, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows. Then the two reads determine the same finite BEDC route through the Real-completion gateway. Conversely, every terminal route available to the current Real-completion open phase is read through exactly those four faces and support rows.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-open-phase-four-face-terminality}. It states that agreement on the StreamName window, DyadicRatCore ledger, RegSeqRat readback, RealUp seal, and displayed support rows determines the same terminal finite BEDC route.

Next use \autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The lattice gives the converse direction: every terminal open-phase route is exhausted by the same four faces and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally compare with \autoref{def:streamname-real-completion-gateway-carrier}. The carrier lists exactly those rows and no additional coordinate. Therefore two gateway reads with the same four faces and support rows determine the same finite BEDC gateway route, and every terminal route in the current Real-completion open phase is read through that packet.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway ordered source readback]
\label{thm:streamname-real-completion-gateway-ordered-source-readback}
Every accepted $\StreamNameUp$ Real-completion gateway read consumes the source in the strict order
$$
S \longrightarrow D \longrightarrow R \longrightarrow E .
$$
The StreamName finite window $S$ is read first, the $\DyadicRatCoreUp$ tolerance ledger $D$ is anchored to that window, the $\RegSeqRatUp$ readback $R$ is available only from $S,D$, and the $\RealUp$ seal $E$ is available only after $R$. The gateway exports no permutation of these four faces, no bypass through $D$, and no direct $S \longrightarrow E$ route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:streamname-real-completion-gateway-carrier}. Its displayed route rows name $S$ before $D$, name $R$ only from the paired $S,D$ read, and name $E$ only after the readback row.

Apply \autoref{thm:streamname-real-completion-gateway-obligations}. The NameCert surface exposes the same ordered rows as the accepted gateway packet, so every consumer reads the four faces through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local naming support.

Use \autoref{thm:streamname-dyadicratcore-window-anchor} to rule out a dyadic bypass. The tolerance ledger is attached to the StreamName window before any RegSeqRat or RealUp consumer can inspect the route.

Finally apply \autoref{thm:streamname-real-completion-gateway-terminality}. Since all terminal Real-completion routes factor through the same four-face packet, a consumer cannot reorder the faces or jump directly from $S$ to $E$ without leaving the exported gateway carrier.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway touchpoint factorization]
\label{thm:streamname-real-completion-gateway-touchpoint-factorization}
Let
$$
G=(S,D,R,E,B,H,C,P,N)
$$
be an accepted $\StreamNameUp$ Real-completion gateway packet whose source readback follows
$$
S \longrightarrow D \longrightarrow R \longrightarrow E .
$$
Then the machine-facing surface of $G$ is exactly the factorization through the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. Equivalently, the only Lean-route positions consumed by the gateway are
$$
\begin{gathered}
\texttt{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_singleton\_diagonal\_handoff},\\
\texttt{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_regseqrat\_bridge\_handoff\_exactness},\\
\texttt{BEDC.Derived.RegSeqRatUp.RegSeqRatStreamCarrier\_real\_seal\_handoff}.
\end{gathered}
$$
The factorization exports no quotient stream equality, host sequence equality, selected limit, ambient $\RealUp$ completeness, metric-completeness data, countable-choice row, standard bridge row, or bridge-row substitute.
\end{theorem}
\begin{proof}
Start with \autoref{thm:streamname-real-completion-gateway-ordered-source-readback}. It fixes the gateway source order as $S$ before $D$, $R$ only from the paired $S,D$ route, and $E$ only after $R$.

Next apply \autoref{thm:streamname-real-completion-gateway-obligations}. The accepted packet exposes exactly the four faces $S,D,R,E$ and the support rows $B,H,C,P,N$, so the gateway has no machine-facing coordinate outside the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ inventory.

Now use \autoref{thm:streamname-real-completion-exit-lean-route-boundary} together with \autoref{thm:streamname-open-phase-lean-touchpoint-triad}. These bind the same four-face exit read to exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. The three touchpoints are route positions for the existing window, ledger, readback, and seal rows, not additional carrier data.

Finally invoke \autoref{thm:streamname-real-completion-gateway-nonescape}. Since every accepted gateway read factors through $S,D,R,E,B,H,C,P,N$, the cited Lean-route boundary cannot introduce quotient stream equality, host sequence equality, selected limits, ambient Real completeness, metric-completeness data, countable choice, a standard bridge row, or any bridge-row substitute. Thus the ordered gateway packet and the three touchpoints form one exact factorization surface.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway status exactness]
\label{thm:streamname-real-completion-gateway-status-exactness}
Let
$$
G=(S,D,R,E,B,H,C,P,N)
$$
be an accepted $\StreamNameUp$ Real-completion gateway packet. The packet is status-exact for the current Phase Real and Completion boundary exactly when the four public status faces are read as the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ closurestatus and formalstatus records, respectively, with only $B,H,C,P,N$ as support rows. No aggregate token, fifth completion object, quotient stream, selected limit, countable-choice row, metric-completeness datum, or standard bridge row can replace any one of the four faces or enter as an additional status face.
\end{theorem}
\begin{proof}
Project the gateway carrier of \autoref{def:streamname-real-completion-gateway-carrier}. Its accepted packet exposes exactly the four faces $S,D,R,E$ and the support rows $B,H,C,P,N$, so status information has no carrier coordinate outside that displayed list.

Use \autoref{thm:streamname-real-completion-gateway-ordered-source-readback}. The gateway reads $S$ before $D$, reads $R$ only from the paired $S,D$ route, and reads $E$ only after $R$. Thus the four status faces cannot be permuted, fused into an aggregate token, or bypassed through a direct completion row.

Apply \autoref{thm:streamname-real-completion-four-object-exit-route} and \autoref{thm:streamname-real-completion-status-ledger-exactness}. These theorems identify the same four Phase Real and Completion faces as the StreamName finite window, DyadicRatCore finite dyadic budget, RegSeqRat regularity handoff, and RealUp seal route.

Finally use the two-axis discipline recorded by the roadmap closurestatus blocks. The closurestatus and formalstatus rows are read per object, while $B,H,C,P,N$ only observe, transport, replay, package, and name the displayed faces. Therefore the gateway is status-exact precisely for those four per-object records, with no extra completion, quotient, choice, metric-completeness, selected-limit, or bridge status row hidden in the route.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway no-choice normal form]
\label{thm:streamname-real-completion-gateway-no-choice-normal-form}
Let
$$
G=(S,D,R,E,B,H,C,P,N)
$$
be an accepted $\StreamNameUp$ Real-completion gateway packet. Every terminal seal consumer or completion-facing consumer of $G$ that is status-exact and machine-facing through the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff has the normal form
$$
S \longrightarrow D \longrightarrow R \longrightarrow E
$$
with support rows $B,H,C,P,N$. Any read mentioning quotient stream equality, host sequence equality, a selected limit, countable choice, ambient $\RealUp$ completeness, metric-completeness data, a standard bridge row, or a bridge-row substitute lies outside the exported gateway carrier.
\end{theorem}
\begin{proof}
Use \autoref{thm:streamname-real-completion-gateway-ordered-source-readback}. It fixes the only consumer order exported by the accepted gateway packet as $S$ before $D$, $R$ only from the paired $S,D$ read, and $E$ only after $R$.

Apply \autoref{thm:streamname-real-completion-gateway-status-exactness}. A status-exact consumer reads the four public status faces as the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ records, while $B,H,C,P,N$ remain support rows rather than additional completion data.

Next use \autoref{thm:streamname-real-completion-gateway-touchpoint-factorization}. The machine-facing route is exactly the three existing touchpoints named in the statement, so no fourth machine coordinate can supply quotient equality, a selected limit, choice, completeness, or bridge data.

Finally invoke \autoref{thm:streamname-real-completion-gateway-nonescape}. Since every accepted gateway read factors through $S,D,R,E,B,H,C,P,N$, any consumer that mentions one of the excluded coordinates has left the exported carrier. Thus every terminal seal or completion-facing consumer that remains inside the gateway has precisely the displayed no-choice normal form.
\end{proof}

\begin{theorem}[StreamName Real-completion gateway support-row minimality]
\label{thm:streamname-real-completion-gateway-support-row-minimality}
Let
$$
G=(S,D,R,E,B,H,C,P,N)
$$
be an accepted $\StreamNameUp$ Real-completion gateway packet for the current Phase Real and Completion boundary. The five support rows $B,H,C,P,N$ are independently necessary for the gateway surface:
\begin{enumerate}
\item without $B$, there is no displayed observation surface for the four faces $S,D,R,E$;
\item without $H$, componentwise transport cannot identify the same finite route through the window, ledger, readback, seal, route, provenance, and local naming rows;
\item without $C$, the ordered route $S \longrightarrow D \longrightarrow R \longrightarrow E$ cannot be replayed inside the packet;
\item without $P$, provenance over the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces is absent;
\item without $N$, the local $\NameCert_{\StreamNameUp}$ row for the four faces and their displayed support is absent.
\end{enumerate}
When the four faces and all five support rows are present, \autoref{thm:streamname-real-completion-gateway-no-choice-normal-form} gives the unique no-choice normal form. The minimality claim exports no quotient stream equality, host sequence equality, selected limit, countable-choice row, ambient $\RealUp$ completeness, metric-completeness data, standard bridge row, or bridge-row substitute.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:streamname-real-completion-gateway-carrier}. It displays exactly the four faces $S,D,R,E$ and the five support rows $B,H,C,P,N$, with no extra coordinate that could replace one of those support rows.

Apply \autoref{thm:streamname-real-completion-gateway-obligations}. The accepted local $\NameCert_{\StreamNameUp}$ surface assigns $B$ to displayed $\BHist$ observation, $H$ to componentwise $\hsame$ transport, $C$ to displayed $\Cont$ route replay, $P$ to $\Pkg$ provenance, and $N$ to local naming. Removing any one row removes exactly the corresponding obligation from the accepted packet surface.

\begin{enumerate}
\item The $B$ row is necessary because the carrier and obligation theorem expose the four faces through displayed $\BHist$ observations. Without $B$, the packet may still name $S,D,R,E$, but it has no displayed observation surface for them.
\item The $H$ row is necessary because the same finite route is compared componentwise through $\hsame$ across the window, ledger, readback, seal, route, provenance, and local naming rows. Without $H$, terminal agreement cannot identify that the read is the same finite route.
\item The $C$ row is necessary by \autoref{thm:streamname-real-completion-gateway-ordered-source-readback}. The source order $S \longrightarrow D \longrightarrow R \longrightarrow E$ is part of the displayed route replay, so deleting $C$ deletes the internal replay of that order.
\item The $P$ row is necessary by \autoref{thm:streamname-real-completion-gateway-touchpoint-factorization}. The machine-facing factorization is over the four named faces and their existing route positions; without $P$, the packet has no provenance tying those faces to the gateway package.
\item The $N$ row is necessary by \autoref{thm:streamname-real-completion-gateway-status-exactness}. Status exactness is read through local $\NameCert_{\StreamNameUp}$ rows for the four faces and their support, so without $N$ the gateway lacks the local naming row that records the status surface.
\end{enumerate}

With all five support rows present, the same carrier, obligation, ordered-readback, factorization, and status-exactness theorems place the accepted packet back inside the hypotheses of \autoref{thm:streamname-real-completion-gateway-no-choice-normal-form}. That theorem returns the unique no-choice normal form for the current gateway.

The exclusions are preserved because none of the five support rows is a quotient stream equality, host sequence equality, selected limit, countable-choice row, ambient Real completeness datum, metric-completeness datum, standard bridge row, or bridge-row substitute, and the no-choice normal form already rejects every read mentioning those coordinates.
\end{proof}
