\section{StreamName Real seal factorization boundary}
\label{sec:streamname-real-seal-factorization-boundary}

\begin{theorem}[StreamName Real seal factorization boundary]
\label{thm:streamname-real-seal-factorization-boundary}
Let $W$ be a finite public $\StreamNameUp$ rational observation window. Suppose
that $W$ is read through certified unary indices, that an accepted
$\RegSeqRat$ pointwise seal package is displayed over the same certified
indices, and that a finite-window $\RealUp$ seal read arises from that
StreamName-to-$\RegSeqRat$ handoff. Then the $\RealUp$ seal read factors
through exactly the following rows: the StreamName point rows over $W$, the
accepted $\RegSeqRat$ seal rows, the $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ membership rows, the $\mathsf{UnaryHistory}$ observation
rows, the finite $\Cont$ ledger, the displayed $\hsame$ transports, and the
$\mathsf{Pkg}$ provenance naming the source certificates.

Conversely, any finite packet consisting of precisely those rows repacks as
the same public finite-window $\RealUp$ seal read. The factorization contains
no completion data, quotient representative, host index equality, Classical
choice, or $\RealUp$ completeness datum outside the displayed
$\RegSeqRat$ seal rows.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.StreamNameRealSealFactorizationBoundary}
\begin{proof}
First read the public $\RealUp$ boundary through
\autoref{thm:streamname-realup-seal-boundary}. This identifies every
finite-window endpoint read arising from the handoff with the StreamName source
rows, the accepted $\RegSeqRat$ pointwise rows, bundle membership, unary
observations, finite ledger entries, $\hsame$ transports, and provenance rows.

Next use \autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. It
prevents nested finite windows from changing the seal surface: restricting or
refining $W$ keeps the same displayed point rows, the same accepted
$\RegSeqRat$ seal rows, and the same finite $\Cont/\mathsf{Pkg}$ provenance
on the certified indices.

The common seal cover is supplied by
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}. The StreamName
window, the $\RegSeqRat$ seal packet, and the $\RealUp$ endpoint read agree
only through the listed rows, so any public $\RealUp$ read from the handoff
has the announced factorization.

Finally apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. The pointwise
handoff exhausts the downstream seal rows by the certified StreamName
observations and accepted $\RegSeqRat$ rows. Since none of the cited boundary
theorems introduces completion data, quotient representatives, host index
equality, Classical choice, or a $\RealUp$ completeness field, the reverse
packing uses exactly the displayed rows and no further datum.
\end{proof}
\leanchecked{BEDC.Derived.StreamNameUp.StreamnameRealSealFactorizationBoundary}

\begin{theorem}[StreamName Real seal factorization refinement stability]
\label{thm:streamname-real-seal-factorization-refinement-stability}
Let $W \subseteq W'$ be finite public $\StreamNameUp$ rational observation
windows related by displayed prefix refinement. Suppose both windows carry
accepted $\RegSeqRat$ seal rows over the certified unary indices, and suppose
the source tuple for $W'$ restricts to the source tuple for $W$ through the same
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, $\Cont$,
$\hsame$, and $\mathsf{Pkg}$ rows. Then the finite-window $\RealUp$ seal
factorization over $W$ is exactly the restriction of the factorization over
$W'$.

The restricted factorization contains no completion datum, quotient
representative, host index equality, choice row, or $\RealUp$ completeness
field beyond the displayed accepted $\RegSeqRat$ seal rows.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-real-seal-factorization-boundary} to both finite
windows. Each factorization is read through the StreamName point rows, the
accepted $\RegSeqRat$ seal rows, bundle membership, unary observations, finite
continuation ledger, displayed $\hsame$ transports, and package provenance.

Use \autoref{thm:streamname-regseqrat-uniform-finite-window-seal} on the prefix
refinement $W \subseteq W'$. It identifies the seal rows on the smaller window
with the restriction of the rows displayed on the larger window.

It remains to identify the source tuple. The determinacy theorem
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy} says the
restricted source is fixed by the displayed StreamName, bundle, history,
transport, continuation, and provenance rows. The minimality theorem
\autoref{thm:streamname-regseqrat-realup-seal-source-minimality} rules out any
extra source coordinate outside those rows.

Therefore restricting the $W'$ factorization along the displayed prefix
refinement gives exactly the factorization obtained directly over $W$, with no
additional completion, quotient, host-equality, choice, or completeness data.
\end{proof}

\begin{theorem}[StreamName Real finite-window classifier exactness]
\label{thm:streamname-real-seal-finite-window-classifier-exactness}
Let $W$ and $W'$ be finite public $\StreamNameUp$ rational observation windows
over certified unary indices. Suppose the two windows display the same
$\mathsf{ProbeBundle}$ rows, the same $\mathsf{InBundle}$ membership rows, the
same $\mathsf{UnaryHistory}$ observations, the same pointwise rational
classifier rows, the same accepted $\RegSeqRat$ seal rows, the same finite
$\Cont$ ledger, the same displayed $\hsame$ transports, and the same
$\mathsf{Pkg}$ provenance naming the source certificates. Then the
finite-window $\RealUp$ seal classifier induced by either window is exactly the
transport of the $\RegSeqRat$ classifier read from those displayed rows.

In particular, no completion representative, quotient equality, hidden host
index equality, choice datum, or $\RealUp$ completeness field can change that
classifier once the listed finite StreamName and $\RegSeqRat$ rows agree.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-real-seal-factorization-boundary}. The boundary
theorem says that every finite-window $\RealUp$ seal classifier arising from
the StreamName-to-$\RegSeqRat$ handoff is read only through the listed
StreamName rows, accepted $\RegSeqRat$ seal rows, bundle membership, unary
history, continuation ledger, $\hsame$ transports, and package provenance.

Next apply
\autoref{thm:streamname-real-seal-factorization-refinement-stability}. Any
common finite presentation or prefix refinement of $W$ and $W'$ restricts to
the same displayed factorization, so changing the window while preserving the
listed rows cannot change the induced $\RealUp$ classifier.

The classifier handoff is the equality supplied by
\autoref{thm:streamname-regseqrat-common-window-transport}. Since the two
windows expose the same pointwise rational classifier rows and the same
accepted $\RegSeqRat$ seal rows, the transported $\RegSeqRat$ classifier is the
single classifier available on the common finite surface.

Finally,
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy} fixes the
source tuple from the displayed StreamName, bundle, history, transport,
continuation, and provenance rows, and
\autoref{thm:streamname-regseqrat-realup-seal-source-minimality} rules out any
extra source coordinate. Hence the finite-window $\RealUp$ seal classifier is
exactly the transported $\RegSeqRat$ classifier read from those rows, with no
escape through completion, quotient, host-equality, choice, or completeness
data.
\end{proof}
