\section{StreamName Real and RegSeqRat handoff}
\label{sec:streamname-real-regseq-handoff}

\begin{theorem}[StreamName finite-window handoff to RegSeqRat and RealUp]
\label{thm:streamname-real-regseq-finite-window-handoff}
Let $\mathcal{W}$ be a public $\StreamNameUp$ finite-window package over
$\Hist$ whose selected observations are certified by a finite
$\mathsf{ProbeBundle}$ ledger and by $\mathsf{InBundle}$ membership rows. Then
the rows handed to $\RegSeqRat$ or finite-window $\RealUp$ consumers are exactly
the selected $\mathsf{RatHistoryClassifier}$ rows, the finite
$\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership rows, and the
$\mathsf{UnaryHistory}$ rows naming the observed histories.

No $\RegSeqRat$ regularity row, no $\RealUp$ seal classifier, no completion
object, and no host equality row is read from $\mathcal{W}$.
\end{theorem}
\begin{proof}
Project the public StreamName boundary through
\autoref{thm:streamname-public-finite-window-interface}. That theorem lists the
carrier, selected classifier, probe-bundle, membership, and unary-history rows
available at the public finite-window interface.

For a finite-window $\RealUp$ consumer, apply
\autoref{thm:realup-finite-window-exhaustion-obligation} and
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. These RealUp
rows consume the displayed finite StreamName packet and its ledger, not a
completion object or a hidden host stream.

For a $\RegSeqRat$ consumer, apply
\autoref{thm:regseqrat-finite-window-seal-exactness}. The seal reads the
selected finite-window classifier and bundle rows as inputs to the downstream
regularity and seal surface. Since the StreamName interface theorem lists no
regularity row and no seal classifier, those obligations remain outside the
handoff.
\end{proof}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_real\_regseq\_handoff}

\begin{theorem}[StreamName singleton RegSeqRat RealUp handoff exactness]
\label{thm:streamname-singleton-regseq-real-handoff-exactness}
Let $s,t:\Hist\to\Hist$ be StreamName streams and let $n:\Hist$ be a
certified unary observation. If $\mathsf{RatStreamNameClassifier}(s,t)$
holds and $n$ is a $\mathsf{UnaryHistory}$ row, then the singleton packet
$\mathsf{ProbeBundle.Bcons}\ n\ \mathsf{ProbeBundle.Bnil}$ supplies the
finite-window StreamName classifier consumed by the $\RegSeqRat$ and
$\RealUp$ handoff.

For that singleton packet, the exported consumer surface is exactly the
selected rational classifier row
$\mathsf{RatHistoryClassifier}(s(n),t(n))$, the singleton
$\mathsf{ProbeBundle}$ row, the corresponding $\mathsf{InBundle}$ ledger
row, the displayed $\mathsf{UnaryHistory}$ row for $n$, and the visible
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\mathsf{NameCert}$ support already
present on the public StreamName side.

The packet exports no $\RegSeqRat$ regularity row, no $\RealUp$
completeness row, no quotient stream, no host sequence equality row, and no
selected limit.
\end{theorem}
\begin{proof}
Use the singleton diagonal handoff shape for rational StreamName classifiers.
It turns the pointwise hypothesis $\mathsf{RatStreamNameClassifier}(s,t)$ and
the certified unary row for $n$ into a
$\mathsf{RatStreamNameFiniteWindowClassifier}$ over
$\mathsf{ProbeBundle.Bcons}\ n\ \mathsf{ProbeBundle.Bnil}$, with membership
given by the singleton $\mathsf{InBundle}$ constructor.

The same shape identifies the only selected classifier row: every member of
the singleton packet is judgmentally the displayed observation $n$, so the
finite-window classifier reads the single row
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ and no second rational-history
coordinate.

Now apply
\autoref{thm:streamname-real-regseq-finite-window-handoff} to this
finite-window package. That theorem lists exactly the rows visible to
$\RegSeqRat$ and finite-window $\RealUp$ consumers: selected rational
classifier data, the finite probe ledger, membership rows, unary-history rows,
and the displayed StreamName support rows.

Since the singleton construction supplies only those rows, all regularity,
completion, quotient, host-equality, and limit data remain outside the
handoff.
\end{proof}

\begin{theorem}[StreamName constant-window handoff boundary]
\label{thm:streamname-real-regseq-constant-boundary}
Let $a,b:\Hist$ be rational-history endpoints and let $\mathcal{W}$ be a
constant rational $\StreamNameUp$ finite-window package over an inhabited
finite unary window. The package may seed the $\RegSeqRat$ stream side only by
exporting the same $\mathsf{RatHistoryClassifier}(a,b)$ row together with its
finite $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$
ledger. A $\RegSeqRat$ certificate must still supply regularity rows, and a
sealed $\RealUp$ candidate must still supply the seal classifier row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-constant-window-real-boundary}. It says that a
finite-window $\RealUp$ consumer of the constant package reads only the rational
point classifier and the finite probe ledger.

Apply \autoref{thm:streamname-constant-window-regseq-boundary}. It gives the
same boundary for $\RegSeqRat$: the constant StreamName window supplies rational
point-classifier and probe-ledger data, while the regularity rows remain
$\RegSeqRat$ obligations.

Finally use \autoref{thm:regseqrat-obligation-seal-ledger} and
\autoref{thm:regseqrat-obligation-seal-interface}. These theorems place
regularity and seal-interface rows on the RegSeqRat and RealUp side of the
boundary, so the constant window is only a seed surface for the displayed finite
rows.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp obligation separation]
\label{thm:streamname-real-regseq-obligation-separation}
Across the StreamName, RegSeqRat, and RealUp handoff, the obligation surface
separates into three disjoint sources. The $\StreamNameUp$ package contributes
the stream carrier, selected rational-history classifier, finite
$\mathsf{ProbeBundle}$ ledger, $\mathsf{InBundle}$ membership, and
$\mathsf{UnaryHistory}$ observation rows. The $\RegSeqRat$ certificate
contributes regularity, dyadic-tolerance, transport, and stream-spine rows. The
$\RealUp$ seal contributes the seal classifier required by the real
classifier specification.

No finite StreamName window contributes a quotient, a completion witness, a
host index equality, a RegSeqRat regularity witness, or the RealUp seal
classifier.
\end{theorem}
\begin{proof}
Read the StreamName part first. By
\autoref{thm:streamname-public-finite-window-interface}, and in the constant
case by \autoref{thm:streamname-constant-window-real-boundary} and
\autoref{thm:streamname-constant-window-regseq-boundary}, the StreamName
surface exposes exactly the carrier, classifier, bundle, membership, unary, and
finite ledger rows.

Read the RegSeqRat part next. The regularity and dyadic-tolerance rows are
listed by \autoref{thm:regseqrat-obligation-seal-ledger}, while
\autoref{thm:regseqrat-finite-window-seal-exactness} describes how the selected
finite-window rows are consumed at the seal boundary.

Read the RealUp part last. The seal classifier is supplied by
\autoref{thm:regseqrat-obligation-seal-interface} and is consumed through
\autoref{thm:realup-finite-window-exhaustion-obligation}. Thus every downstream
row is accounted for by exactly one side of the handoff, and no completion or
host equality row is imported from the finite StreamName package.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-Real seal composition]
\label{thm:streamname-regseqrat-real-seal-composition}
Let $\mathcal{W}$ be a public $\StreamNameUp$ finite-window package whose
selected finite rows are certified by the displayed
$\mathsf{RatHistoryClassifier}$, $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, $\hsame$, finite $\Cont$, and
$\Pkg$ provenance data. Let $S$ be a $\RegSeqRatUp$ finite-window seal that
consumes exactly those selected rational-history rows together with its
regularity, dyadic-tolerance, transport, stream-spine, and seal-interface
ledger rows. Let $R$ be a finite-window $\RealUp$ ledger-boundary row that
consumes the seal $S$.

Then every Real-facing consumer row of $R$ factors through exactly the selected
finite rows of $\mathcal{W}$, the $\RegSeqRat$ regularity,
dyadic-tolerance, transport, stream-spine, and seal rows of $S$, and the
$\RealUp$ seal-classifier ledger row. Conversely, those three displayed
surfaces repack into the same Real-facing finite-window ledger boundary.

The composed route exports no quotient stream, selected host limit, host
equality, completion witness, countable-choice schedule, or ambient
completeness coordinate.
\end{theorem}
\begin{proof}
First isolate the source rows. Apply
\autoref{thm:streamname-real-regseq-finite-window-handoff}. It says that the
public StreamName window contributes only the selected rational-history
classifier rows, the finite probe ledger, bundle-membership rows, unary
observations, finite transport data, and provenance rows.

Next seal those rows on the RegSeqRat side. Use
\autoref{thm:regseqrat-finite-window-seal-exactness} to read the selected
finite classifier rows as the input surface of $S$, and use
\autoref{thm:regseqrat-obligation-seal-interface} to place the regularity,
dyadic-tolerance, transport, stream-spine, and seal-interface rows on the
RegSeqRat ledger side of the boundary.

Finally pass to the Real-facing row. Apply
\autoref{thm:realup-finite-window-exhaustion-obligation} and
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. These theorems
consume the RegSeqRat seal as a finite ledger boundary and expose only the
seal-classifier row required by the RealUp consumer.

The preceding three steps give the forward factorization. The converse
repacking follows by reading the same cited theorems in order: the StreamName
finite rows supply the source packet, the RegSeqRat exactness and interface
rows rebuild the seal packet, and the RealUp boundary theorem rebuilds the
finite-window ledger row. Since each cited boundary excludes quotient streams,
host equalities, completion witnesses, countable-choice schedules, and ambient
completeness coordinates, the composed route exports none of them.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-Real finite-window seal pullback]
\label{thm:streamname-regseqrat-real-finite-window-seal-pullback}
Let $\mathcal{W}$ be a public $\StreamNameUp$ finite-window package whose
selected rational classifier rows are consumed both by a $\RegSeqRatUp$
finite-window seal $S$ and by a finite-window $\RealUp$ seal boundary $R$.
Assume the two consumers read the same displayed finite rows of
$\mathcal{W}$: the $\mathsf{ProbeBundle}$ ledger, $\mathsf{InBundle}$
membership rows, $\mathsf{UnaryHistory}$ observations, selected
$\mathsf{RatHistoryClassifier}$ rows, displayed $\hsame$ comparisons, finite
$\Cont$ routes, $\Pkg$ provenance, and $\NameCert$ support.

Then the common consumer surface of $\mathcal{W}$, $S$, and $R$ is exactly
that finite displayed surface. Equivalently, the $\RegSeqRatUp$ seal and the
finite-window $\RealUp$ seal pull back along the selected $\StreamNameUp$
window to the single cover-indexed boundary carried by those
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
$\mathsf{RatHistoryClassifier}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows.

The pullback boundary introduces no quotient stream, host index equality,
selected limit, ambient completion, or additional $\RealUp$ seal classifier
outside the displayed finite-window ledger.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-real-regseq-finite-window-handoff}. It identifies the
only rows exported by the public StreamName finite window to RegSeqRat and
RealUp consumers: the selected rational classifier rows, probe-bundle ledger,
membership rows, unary observations, finite transport rows, provenance, and
displayed public support. Thus both consumers start from the same finite
StreamName surface.

Next use
\autoref{thm:streamname-real-regseq-obligation-separation}. The separation
places carrier, classifier, bundle, membership, and unary-history data on the
StreamName side; regularity, dyadic-tolerance, transport, and stream-spine
data on the RegSeqRat side; and the seal-classifier obligation on the RealUp
side. Hence no obligation is counted twice, and no quotient, host equality,
limit, or completion row can enter through the shared source.

Finally apply
\autoref{thm:streamname-regseqrat-real-seal-composition}. The composition
theorem repacks the StreamName finite rows, the RegSeqRat seal rows, and the
RealUp seal boundary into one Real-facing finite-window ledger. Since the two
consumers were assumed to read the same displayed finite rows, this
cover-indexed ledger is the required pullback boundary, with no additional
RealUp seal classifier outside the displayed surface.
\end{proof}

\begin{definition}[StreamName-RegSeqRat scheduled seal package]
\label{def:streamname-regseqrat-scheduled-seal-package}
A $\StreamNameUp$--$\RegSeqRat$ scheduled seal package is the scheduled
constant observation row together with three finite-window boundary rows:
\begin{enumerate}
  \item the public finite-window $\StreamNameUp$ row over
  $\mathsf{BHist}$ histories, its finite $\mathsf{ProbeBundle}$ ledger,
  $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ observation
  rows, and the displayed $\hsame$ comparisons between scheduled endpoints;
  \item the $\RegSeqRat$ finite-window seal row reading the same selected
  $\mathsf{RatHistoryClassifier}$ rows and dyadic ledger rows;
  \item the finite-window $\RealUp$ ledger-boundary row that consumes only the
  selected rational classifier rows, the probe ledger, and the unary
  observation rows.
\end{enumerate}
The package has no further carrier. Its consumer-facing surface is exactly the
scheduled observation, finite-window StreamName row, RegSeqRat seal row, and
RealUp ledger-boundary row over the displayed $\mathsf{BHist}$,
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
$\hsame$, $\RatUp$ classifier, and dyadic ledger data.
\end{definition}

\begin{theorem}[StreamName-RegSeqRat scheduled seal exhaustion]
\label{thm:streamname-regseqrat-scheduled-seal-exhaustion}
Every consumer row of the scheduled seal package of
\autoref{def:streamname-regseqrat-scheduled-seal-package} is projected from
exactly one of the following sources: the scheduled constant observation
exactness row, the scheduled window reindex row, the $\RegSeqRat$
finite-window seal exactness row, or the finite-window $\RealUp$
ledger-boundary row. Conversely, those four source rows repack into the
scheduled seal package and determine its whole consumer-facing surface.

No consumer row of the package exports completion data, quotient data, host
index equality, a $\RegSeqRat$ regularity witness beyond the finite-window seal
row, or a $\RealUp$ seal classifier outside the displayed ledger boundary.
\end{theorem}
\begin{proof}
First project the scheduled StreamName source. Apply
\autoref{thm:streamname-constant-scheduled-observation-exactness} to obtain
the constant observation row and
\autoref{thm:streamname-scheduled-window-reindex-stability} to identify its
finite scheduled windows under reindexing.

Next project the downstream seal rows. The finite-window feed theorem
\autoref{thm:streamname-regseqrat-realup-finite-window-feed} places the
selected $\RatUp$ classifier rows, probe-bundle rows, membership rows, unary
observation rows, and dyadic ledger rows at the common handoff. The RegSeqRat
seal scope theorem \autoref{thm:streamname-regseqrat-seal-scope} says that
the RegSeqRat consumer reads precisely the finite-window seal row from that
handoff.

The separation theorems in this section identify the remaining boundary.
\autoref{thm:streamname-real-regseq-finite-window-handoff} gives the public
finite-window StreamName row, \autoref{thm:streamname-real-regseq-constant-boundary}
specializes it to the constant scheduled source, and
\autoref{thm:streamname-real-regseq-obligation-separation} keeps the
RegSeqRat and RealUp obligations disjoint.

For the reverse direction, repack the scheduled observation exactness row,
the reindex row, the RegSeqRat finite-window seal exactness row, and the
RealUp finite-window ledger boundary into the three displayed components of
\autoref{def:streamname-regseqrat-scheduled-seal-package}. The same cited
handoff and separation theorems exclude every row outside those components, so
the repacked package is exhaustive.
\end{proof}

\input{parts/concrete_instances/streamname/real_regseq_overlap_pasting}

\begin{theorem}[StreamName RegSeqRat overlap-pasting consumer exhaustion]
\label{thm:streamname-regseqrat-overlap-pasting-consumer-exhaustion}
Let $\mathcal{W}_0$ and $\mathcal{W}_1$ be certified finite
$\StreamNameUp$ windows with certified finite overlap $K$. Suppose the
hypotheses of
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting} hold: the two
restrictions to $K$ agree on the certified unary observations, selected
$\mathsf{RatHistoryClassifier}$ rows, $\mathsf{ProbeBundle}$ ledger rows,
$\mathsf{InBundle}$ membership rows, displayed $\hsame$ rows, and the induced
$\RegSeqRat$ handoffs consume the same DyadicRatCore finite ledger on $K$.
Then every finite-window $\RealUp$ consumer row read from
$\mathcal{W}_0 \cup \mathcal{W}_1$ is exactly one of the following rows: a row
already read from $\mathcal{W}_0$, a row already read from $\mathcal{W}_1$, or
an overlap row identified by
\autoref{thm:streamname-regseqrat-pointwise-seal-stability}.

Thus the exhausted consumer surface is precisely the finite inventory of
$\mathsf{RatHistoryClassifier}$ rows, $\mathsf{ProbeBundle}$ rows,
$\mathsf{InBundle}$ rows, $\mathsf{UnaryHistory}$ rows, $\hsame$ comparisons,
and shared DyadicRatCore ledger rows. It contains no completion datum, quotient
datum, host-index equality, metric row, or $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
First paste the seal surface. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting}. Its hypotheses are
the displayed agreement rows on $K$ together with the common DyadicRatCore
finite ledger, so it yields one pasted finite-window source surface over
$\mathcal{W}_0 \cup \mathcal{W}_1$.

Next compare the consumer rows on the overlap. By
\autoref{thm:streamname-real-regseq-common-window-consumer-determinacy}, any
finite-window $\RealUp$ consumer restricted to $K$ reads the same
$\mathsf{BHist}$ surface as the induced $\RegSeqRat$ handoff. The pointwise
identifications on $K$ are exactly those supplied by
\autoref{thm:streamname-regseqrat-pointwise-seal-stability}.

Now run finite bundle induction over the two windows. A selected row outside
$K$ is inserted from the unique source window containing it. A selected row
inside $K$ is identified through the overlap comparison, so inserting it from
either side gives the same pasted consumer row.

Finally apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion} to the pasted
surface. It enumerates the only rows visible to $\RegSeqRat$ and finite-window
$\RealUp$ consumers: rational-history classifier rows, bundle and membership
rows, unary observations, $\hsame$ comparisons, and the shared dyadic ledger.
The exclusion clause rules out completion, quotient, host-index, metric, and
RealUp-completeness data, so the union consumer surface is exhausted exactly by
the stated rows.
\end{proof}

\begin{theorem}[StreamName RegSeqRat three-window seal coherence]
\label{thm:streamname-regseqrat-three-window-seal-coherence}
Let $\mathcal{W}_0$, $\mathcal{W}_1$, and $\mathcal{W}_2$ be certified finite
$\StreamNameUp$ windows with certified finite pairwise overlaps. Suppose that
on every displayed overlap the selected $\mathsf{RatHistoryClassifier}$ rows,
$\mathsf{ProbeBundle}$ ledger rows, $\mathsf{InBundle}$ membership rows,
$\mathsf{UnaryHistory}$ observations, displayed $\hsame$ comparisons, and
DyadicRatCore finite ledger rows are compatible. Then the finite-window
$\RealUp$ seal source surface obtained by pasting
$(\mathcal{W}_0 \cup \mathcal{W}_1) \cup \mathcal{W}_2$ is the same source
surface as the one obtained by pasting
$\mathcal{W}_0 \cup (\mathcal{W}_1 \cup \mathcal{W}_2)$.

The common surface is exhausted by the displayed finite StreamName,
$\RegSeqRat$, and DyadicRatCore rows. No completion datum, quotient datum, host
index equality, metric-completeness row, Classical principle, or ambient
model datum enters the comparison.
\end{theorem}
\begin{proof}
First compare the sources on each pairwise overlap. Apply
\autoref{thm:streamname-real-regseq-overlap-unique-source} to the certified
restrictions of $\mathcal{W}_0$ and $\mathcal{W}_1$, then to the restrictions
of $\mathcal{W}_1$ and $\mathcal{W}_2$, and then to the restrictions of
$\mathcal{W}_0$ and $\mathcal{W}_2$. Each comparison is witnessed by the same
displayed unary observations, selected classifier rows, bundle rows,
membership rows, and $\hsame$ rows carried by the pairwise overlap.

Next stabilize the seal rows pointwise. Use
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} on each overlap.
The shared DyadicRatCore finite ledger rows force the induced $\RealUp$ seal
rows to agree wherever two windows meet.

Now paste in the left-associated order. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting} to
$\mathcal{W}_0$ and $\mathcal{W}_1$, and then apply the same theorem to the
pasted surface and $\mathcal{W}_2$. The second application uses the pairwise
overlap identifications already obtained to identify every row in
$(\mathcal{W}_0 \cup \mathcal{W}_1) \cap \mathcal{W}_2$.

Paste in the right-associated order by the symmetric construction. The same
pasting theorem first combines $\mathcal{W}_1$ with $\mathcal{W}_2$ and then
combines $\mathcal{W}_0$ with that surface. Because every overlap row has
already been identified by source uniqueness and pointwise seal stability, no
new row can distinguish the two bracketings.

Finally exhaust both pasted surfaces. Apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion} to the
left-associated surface and again to the right-associated surface. Both
surfaces contain exactly the displayed finite rows listed in the theorem and
therefore present the same source-facing $\RealUp$ seal surface.
\end{proof}

\begin{theorem}[StreamName Real-RegSeq common-window consumer determinacy]
\label{thm:streamname-real-regseq-common-window-consumer-determinacy}
Let $\mathcal{W}_0$ and $\mathcal{W}_1$ be public $\StreamNameUp$
finite-window packages restricting to a certified finite overlap $K$. Suppose
that the restrictions agree on every pointwise $\mathsf{RatStreamNameCarrier}$
observation, every pointwise $\mathsf{RatStreamNameClassifier}$ observation,
the finite $\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership
rows, the certified $\mathsf{UnaryHistory}$ observations, the displayed
$\hsame$ rows, and the consumed DyadicRatCore finite ledger over $K$.

Then every induced $\RegSeqRat$ handoff and every finite-window $\RealUp$
handoff determined by those packages has the same consumer-facing finite
$\mathsf{BHist}$ surface on $K$. That surface is exhausted by the public
$\StreamNameUp$ rows together with the $\RegSeqRat$ and DyadicRatCore finite
rows named above, and it contains no quotient datum, completion datum, host
index equality, metric-completeness row, Classical datum, or standard-bridge
datum.
\end{theorem}
\begin{proof}
First identify the source. Apply
\autoref{thm:streamname-real-regseq-overlap-unique-source} to the two public
finite-window restrictions on $K$. The hypotheses list the same pointwise
carrier rows, classifier rows, bundle ledger, membership rows, unary
observations, and displayed $\hsame$ comparisons, so both packages expose one
source-facing StreamName surface on the overlap.

Next stabilize the seal classifier rows. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability}. The common
DyadicRatCore finite ledger is exactly the downstream input used by the
induced $\RegSeqRat$ handoffs, so the finite-window $\RealUp$ seal rows agree
pointwise over the same overlap.

Finally exhaust the consumer surface with
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. Every row a
$\RegSeqRat$ or finite-window $\RealUp$ consumer can read is one of the public
StreamName point rows, the bundle and membership rows, the unary observation
rows, the displayed $\hsame$ rows, or the shared DyadicRatCore ledger rows.
The exclusion clause of that theorem rules out any remaining quotient,
completion, host-index, metric-completeness, Classical, or standard-bridge
datum.
\end{proof}

\begin{theorem}[StreamName RegSeqRat visible-row exhaustion]
\label{thm:streamname-regseqrat-visible-row-exhaustion}
Every finite-window row handed from $\StreamNameUp$ to a $\RegSeqRat$ consumer
or to a finite-window $\RealUp$ consumer is exactly one of the pointwise
$\mathsf{RatStreamNameCarrier}$ and $\mathsf{RatStreamNameClassifier}$
observations at certified $\mathsf{UnaryHistory}$ indices, one of the displayed
componentwise $\hsame$ rows, one of the consumed $\DyadicRatCoreUp$ finite
ledger rows over the same finite window, one of the finite
$\mathsf{ProbeBundle}$ ledger rows, or one of the $\mathsf{InBundle}$ membership
rows naming the selected observations. Conversely, these pointwise
carrier/classifier rows, componentwise comparison rows, dyadic finite ledger
rows, bundle ledger rows, and membership rows repack into the same
consumer-facing handoff surface.
\end{theorem}
\begin{proof}
Project the finite-window handoff with
\autoref{thm:streamname-real-regseq-finite-window-handoff}. The projection lists
exactly the selected rational-history classifier rows, the finite
$\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership rows, the
certified $\mathsf{UnaryHistory}$ observation rows, the displayed $\hsame$
comparisons, and the consumed DyadicRatCore finite ledger over the same finite
window.

Identify the source rows pointwise using \autoref{def:rat-stream-name-carrier}
and \autoref{def:rat-stream-name-classifier}. The restriction and exhaustion
steps are supplied by \autoref{thm:rat-stream-name-finite-window-from-classifier}
and \autoref{thm:rat-stream-name-finite-window-exhausts-classifier}, so the
finite-window rows are exactly the certified unary-index observations and their
selected bundle support.

Finally use
\autoref{thm:streamname-real-regseq-common-window-consumer-determinacy}. It
keeps the consumed DyadicRatCore rows and the displayed $\hsame$ rows on the
same public window. Repacking the listed rows through the same finite-window
handoff theorem returns the original consumer-facing surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat no-extra-data exclusion]
\label{thm:streamname-regseqrat-no-extra-data-exclusion}
The finite-window handoff surface from $\StreamNameUp$ to a $\RegSeqRat$
consumer or to a finite-window $\RealUp$ consumer contains no host index
equality, quotient datum, completion datum, metric-completeness row, Classical
datum, standard-bridge row, selected limit, or ambient $\RealUp$ completeness
row. $\RegSeqRat$ regularity and the $\RealUp$ seal classifier remain downstream
obligations, while the DyadicRatCore ledger, displayed $\hsame$ rows, finite
bundle ledger, and membership rows are the visible finite handoff data.
\end{theorem}
\begin{proof}
Start from
\autoref{thm:streamname-real-regseq-obligation-separation}. It separates the
source-facing StreamName rows from downstream $\RegSeqRat$ regularity and
finite-window $\RealUp$ seal obligations, so neither downstream obligation can
be read as hidden StreamName source data.

Use \autoref{thm:streamname-real-regseq-overlap-unique-source} on the same
finite window. The unique-source clause rules out alternate host-index,
quotient, or completion coordinates for a surface with the displayed pointwise
rows, comparisons, bundle rows, membership rows, and finite ledger.

The finite-window handoff theorem
\autoref{thm:streamname-real-regseq-finite-window-handoff} supplies only the
listed public rows, and
\autoref{thm:streamname-real-regseq-common-window-consumer-determinacy} keeps
the consumed DyadicRatCore ledger on that window. No metric-completeness row,
Classical datum, bridge row, selected limit, or ambient $\RealUp$ completeness
row is introduced by these finite constructors.
\end{proof}

\begin{theorem}[StreamName RegSeqRat pointwise handoff exhaustion]
\label{thm:streamname-regseqrat-pointwise-handoff-exhaustion}
Every finite-window row handed from $\StreamNameUp$ to a $\RegSeqRat$ consumer
or to a finite-window $\RealUp$ consumer is exhausted by the pointwise
$\mathsf{RatStreamNameCarrier}$ and $\mathsf{RatStreamNameClassifier}$
observations at certified $\mathsf{UnaryHistory}$ indices, the displayed
componentwise $\hsame$ rows, the consumed DyadicRatCore finite ledger rows over
the same finite window, the finite $\mathsf{ProbeBundle}$ ledger, and the
$\mathsf{InBundle}$ membership rows naming the selected observations.
Conversely, those pointwise observations, displayed comparison rows, dyadic
ledger rows, and finite bundle rows repack into the same handoff surface.

The StreamName side contributes no host index equality, quotient data,
completion data, metric-completeness row, Classical datum, or standard-bridge
datum. $\RegSeqRat$ regularity and the $\RealUp$ seal classifier remain
downstream obligations, while the DyadicRatCore ledger and displayed $\hsame$
rows are part of the visible finite handoff surface.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.StreamNameRegSeqRatPointwiseHandoffExhaustion}
\begin{proof}
Apply \autoref{thm:streamname-regseqrat-visible-row-exhaustion}. Its proof
projects the handoff through \autoref{thm:streamname-real-regseq-finite-window-handoff},
then identifies the pointwise carrier and classifier rows by
\autoref{def:rat-stream-name-carrier},
\autoref{def:rat-stream-name-classifier},
\autoref{thm:rat-stream-name-finite-window-from-classifier}, and
\autoref{thm:rat-stream-name-finite-window-exhausts-classifier}.

The same visible-row theorem uses
\autoref{thm:streamname-real-regseq-common-window-consumer-determinacy} to keep
the displayed $\hsame$ comparisons and consumed DyadicRatCore ledger on the
same finite window. Thus the listed rows exhaust the consumer-facing surface
and repack into that surface.

Apply \autoref{thm:streamname-regseqrat-no-extra-data-exclusion}. Its proof
uses \autoref{thm:streamname-real-regseq-obligation-separation} and
\autoref{thm:streamname-real-regseq-overlap-unique-source} to keep downstream
regularity, the finite-window $\RealUp$ seal, host-index equality, quotient
data, completion data, metric-completeness rows, Classical data, standard-bridge
rows, selected limits, and ambient $\RealUp$ completeness outside the source
handoff.
\end{proof}

\input{parts/concrete_instances/streamname/real_regseq_tail_budget_finality}

\begin{theorem}[StreamName RegSeqRat finite-window cover determinacy]
\label{thm:streamname-regseqrat-finite-window-cover-determinacy}
Let $\{W_i\}_{i\in I}$ be a finite public $\StreamNameUp$ cover of rational
windows feeding the same $\RegSeqRat$ finite-window consumer and the same
finite-window $\RealUp$ handoff surface. Suppose every displayed pairwise
overlap satisfies the overlap-source and nested-window determinacy hypotheses
for the StreamName source rows, and suppose every three-way overlap is
compatible in the triple seal cover. Then the induced $\RegSeqRat$ seal rows
and finite-window $\RealUp$ handoff rows determine one cover-indexed source
surface: the selected $\mathsf{RatHistoryClassifier}$ rows, the
$\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership rows,
$\mathsf{UnaryHistory}$ observations, and the displayed $\hsame$ comparisons.

The determined surface contains no completion datum, quotient datum, host
index equality, RegSeqRat regularity claim outside the finite seal rows, or
$\RealUp$ seal classifier outside the displayed ledger boundary.
\end{theorem}
\begin{proof}
Use \autoref{thm:streamname-real-regseq-finite-overlap-source-stability} and
\autoref{thm:streamname-real-regseq-overlap-unique-source} on each displayed
pairwise overlap. They identify the source row, unary observation, bundle
membership, and $\hsame$ comparison read by the two windows.

Induct over the finite cover. The empty and singleton cases are just the
displayed window rows. In the step case, apply
\autoref{thm:streamname-regseqrat-nested-window-seal-determinacy} to paste the
new window into the already determined finite surface along the pairwise
overlap.

For compatibility of the pasted overlaps, use
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}. The triple cover
keeps the StreamName, RegSeqRat, and RealUp reads on the same finite ledger, so
no completion, quotient, host-index, external regularity, or off-ledger
classifier row is introduced.
\end{proof}

\begin{theorem}[StreamName RegSeqRat cover Real handoff descent]
\label{thm:streamname-regseqrat-cover-real-handoff-descent}
Let $\{W_i\}_{i\in I}$ be a finite public $\StreamNameUp$ cover feeding one
$\RegSeqRat$ finite-window consumer and one finite-window $\RealUp$ endpoint.
Suppose that every displayed pairwise overlap satisfies the overlap-source
hypotheses and the nested-window handoff hypotheses, that every nested pair
satisfies seal determinacy, and that every displayed triple overlap satisfies
the triple seal cover. Then the induced $\RealUp$ finite-window handoff descends
to the single cover-indexed source surface determined by
\autoref{thm:streamname-regseqrat-finite-window-cover-determinacy}.

The visible rows are exactly the selected $\mathsf{RatHistoryClassifier}$ rows,
the $\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership rows,
$\mathsf{UnaryHistory}$ observations, displayed $\hsame$ comparisons,
$\mathsf{DyadicRatCore}$ finite ledger rows, and the endpoint seal rows licensed
by the triple cover. The descent contains no completion data, quotient
representatives, host index equality, countable choice, ambient completeness, or
off-ledger $\RealUp$ seal classifiers.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-finite-window-cover-determinacy} to the finite
public cover. Its conclusion supplies a single cover-indexed StreamName source
surface for the selected classifier rows, bundle ledger, membership rows, unary
observations, and displayed $\hsame$ comparisons.

Next stabilize the endpoint-facing seal rows on nested overlaps. By
\autoref{thm:streamname-regseqrat-nested-window-seal-determinacy}, two nested
routes reading the same $\mathsf{DyadicRatCore}$ finite ledger induce the same
finite-window $\RealUp$ seal classifier row on every certified subwindow.

Now compare triples. The compatibility hypothesis feeds
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}, so the StreamName
source rows, the $\RegSeqRat$ finite ledger, and the $\RealUp$ endpoint seal
rows read the same public package on each displayed three-way overlap.

Finally exhaust the consumer-visible surface with
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. Every row seen
by the $\RegSeqRat$ consumer or by the finite-window $\RealUp$ endpoint is one of
the listed source, ledger, membership, observation, comparison, finite
$\mathsf{DyadicRatCore}$, or licensed endpoint-seal rows. The exclusion clauses
in the cover, nested-window, triple-cover, and exhaustion theorems rule out
completion data, quotient representatives, host index equality, countable
choice, ambient completeness, and off-ledger $\RealUp$ seal classifiers.
\end{proof}

\begin{theorem}[StreamName RegSeqRat cover Real four-face exit descent]
\label{thm:streamname-regseqrat-cover-real-four-face-exit-descent}
Let $\{W_i\}_{i\in I}$ be a finite public $\StreamNameUp$ cover satisfying the
hypotheses of
\autoref{thm:streamname-regseqrat-cover-real-handoff-descent}. If the induced
$\RealUp$ endpoint is consumed by a current Phase Real and Completion read,
then that consumer factors through exactly the four displayed faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
together with the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows on the cover-indexed surface.

The factorization contains no quotient stream, no selected limit, no countable
choice row, no ambient $\RealUp$ completeness row, no metric-completeness datum,
no host sequence equality, and no standard bridge row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-cover-real-handoff-descent}. It descends the
finite-window $\RealUp$ handoff to the single cover-indexed StreamName source
surface, with the selected classifier rows, bundle ledger, membership rows,
unary observations, displayed $\hsame$ comparisons, dyadic ledger rows, and
endpoint seal rows all on one public package.

Next invoke \autoref{thm:streamname-four-object-exit-exactness}. The descended
endpoint is therefore read as the same four-object exit route: the finite
$\StreamNameUp$ window, the $\DyadicRatCoreUp$ observation ledger, the
$\RegSeqRatUp$ readback, and the $\RealUp$ seal boundary. No additional
top-level Real-and-completion coordinate is introduced.

Now use \autoref{thm:streamname-open-phase-exit-boundary},
\autoref{thm:streamname-open-phase-four-face-terminality}, and
\autoref{thm:streamname-open-phase-four-face-exit-readback}. These identify the
current Phase Real and Completion exit packet with exactly the four displayed
faces and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
support rows. Thus the cover descent and the current open-phase exit packet
have the same finite BEDC surface.

Finally apply
\autoref{thm:streamname-open-phase-no-fifth-object-exhaustion}. Its exclusion
clauses, together with the exclusions in the cover descent and four-object
exactness theorems, rule out quotient streams, selected limits, countable
choice, ambient $\RealUp$ completeness, metric completeness, host sequence
equality, and bridge rows. Hence every current consumer of the descended
endpoint factors through the four-face exit surface and through no larger
object.
\end{proof}

\input{parts/concrete_instances/streamname/terminal_pullback_factorization}
\input{parts/concrete_instances/streamname/finite_window_route_factorization}
