\begin{theorem}[StreamName RegSeqRat nested-window handoff]
\label{thm:streamname-regseqrat-nested-window-handoff}
Let $K \subseteq J \subseteq L$ be certified finite windows of a public
$\StreamNameUp$ rational stream package. For any $\RegSeqRat$ consumer, and
for any finite-window $\RealUp$ consumer, the source surface obtained by first
restricting the handoff from $L$ to $J$ and then from $J$ to $K$ is the same
source surface as the handoff obtained by restricting directly from $L$ to
$K$.

The common source surface consists only of the pointwise
$\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ observations at certified
$\mathsf{UnaryHistory}$ indices, the finite $\mathsf{ProbeBundle}$ ledger,
the $\mathsf{InBundle}$ membership rows, and the displayed $\hsame$
comparisons. It contains no $\RegSeqRat$ regularity datum, $\RealUp$ seal
datum, completion datum, quotient datum, or host index equality.
\end{theorem}
\begin{proof}
First restrict the outer window. By
\autoref{thm:streamname-real-regseq-finite-window-handoff}, the handoff from
$L$ to $J$ exposes only the selected rational-stream point rows, the finite
bundle ledger, the membership rows, and the displayed $\hsame$ comparisons.
Applying the same theorem again to the certified subwindow $K \subseteq J$
projects the two-step handoff to that same kind of surface over $K$.

Now compare the direct route. Applying
\autoref{thm:streamname-real-regseq-finite-window-handoff} directly to
$K \subseteq L$ gives a handoff surface whose visible rows are again exactly
the certified pointwise carrier and classifier observations, the finite
$\mathsf{ProbeBundle}$ ledger, the $\mathsf{InBundle}$ membership rows, and
the displayed $\hsame$ comparisons over $K$.

Use \autoref{thm:streamname-real-regseq-overlap-unique-source} first on the
overlap $J$ and then on the overlap $K$. The hypotheses are the same certified
point rows and the same finite ledger rows inherited from $L$, so the two
restriction routes cannot produce different StreamName source surfaces on
either overlap.

Finally apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. It collapses
both restricted handoffs to the same pointwise
$\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ rows together with the same finite ledger.
The exclusion clauses in that exhaustion theorem and in the finite-window
handoff theorem keep regularity, seal, completion, quotient, and host-index
data outside the common surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat nested-window seal determinacy]
\label{thm:streamname-regseqrat-nested-window-seal-determinacy}
Let $K \subseteq J \subseteq L$ be certified finite windows of a public
$\StreamNameUp$ rational stream package. Suppose the $\RegSeqRat$ handoff
consumes the same $\mathsf{DyadicRatCore}$ finite ledger along the direct
restriction route from $L$ to $K$ and along the two-step restriction route from
$L$ to $J$ and then from $J$ to $K$. Then the induced finite-window $\RealUp$
seal classifier rows agree on every certified index of $K$.

The common seal row is determined only by the pointwise
$\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ rows, the accepted
$\mathsf{DyadicRatCore}$ ledger entries over $K$, the displayed $\hsame$
transports, the finite $\Cont$ routes, and the shared $\Pkg$ provenance. It
does not use completion data, quotient representatives, host-index equality,
or any $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
First compare the two restriction routes at the StreamName source level. By
\autoref{thm:streamname-regseqrat-nested-window-handoff}, the direct route
$L$ to $K$ and the two-step route through $J$ expose the same pointwise source
rows and the same finite ledger over $K$.

Next transport those rows to the seal side. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} at each certified
index of $K$. Since the carrier row, classifier row, $\hsame$ transport,
$\Cont$ route, $\Pkg$ provenance, and $\mathsf{DyadicRatCore}$ ledger entry are
the same on both routes, the corresponding $\RealUp$ seal classifier row is the
same at that index.

Finally use
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. It says that
the RegSeqRat consumer has no additional public handoff data beyond those
pointwise rows and finite ledger entries. The exclusion clauses in the handoff
and stability theorems keep completion, quotient, host-index, and
$\RealUp$-completeness data outside the determinacy claim, so the rowwise
agreement over $K$ is exactly the stated finite-window seal determinacy.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp triple seal cover]
\label{thm:streamname-regseqrat-realup-triple-seal-cover}
Let $\mathcal{S}$ be an accepted finite $\StreamNameUp$ rational-window
package, let $\mathcal{R}$ be the $\RegSeqRat$ pointwise seal package read from
the same certified unary indices, and let $\mathcal{E}$ be the $\RealUp$
sealing endpoint reached by the finite-window consumer. Then $\mathcal{S}$,
$\mathcal{R}$, and $\mathcal{E}$ determine the same public read exactly when
their unary observation rows, finite $\Cont$ ledger, $\hsame$ endpoint
transports, and $\Pkg$ provenance rows agree.

Equivalently, the three-way cover contains only the pointwise
$\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ observations, the accepted
$\RegSeqRat$ pointwise seal rows, the $\RealUp$ endpoint seal row, the finite
transport ledger, and the shared provenance package. It contains no quotient
representative, completion modulus, host index equality, or additional
regularity datum beyond those rows.
\end{theorem}
\begin{proof}
First compare the $\StreamNameUp$ and $\RegSeqRat$ sides pointwise. By
\autoref{thm:streamname-regseqrat-pointwise-seal-stability}, agreement of the
unary observations, $\hsame$ transports, finite $\Cont$ rows, and $\Pkg$
provenance preserves the accepted seal row at each certified index.

Next paste the pointwise seals. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting} to the certified
finite window. The pasted package has exactly the pointwise rows and the shared
finite ledger, so it is independent of any extra quotient or completion
representative.

Now exhaust the visible handoff. By
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}, every public
row read by the RegSeqRat consumer is one of the displayed unary observation,
transport, ledger, or provenance rows. Thus the RegSeqRat package contributes
no additional public datum once those rows agree.

Finally use \autoref{thm:streamname-regseqrat-nested-window-handoff}. It
identifies the finite-window route to the $\RealUp$ sealing endpoint with the
same restricted source surface. Therefore the StreamName window package, the
RegSeqRat pointwise seal package, and the RealUp endpoint seal determine one
public read exactly in the stated agreement conditions, and the reverse
direction reads the same four families of rows back into the three packages.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp tail-selector factorization]
\label{thm:streamname-regseqrat-realup-tail-selector-factorization}
Every accepted finite-window $\StreamNameUp$ handoff whose $\RegSeqRat$
carrier supplies the scheduled-window projection and whose $\RealUp$ endpoint
read uses finite-prefix exactness factors the tail-selector read through exactly
three public rows: the $\StreamNameUp$ finite-window classifier row, the
$\RegSeqRat$ scheduled projection and readback row, and the $\RealUp$
finite-prefix classifier row.

The factorization exports no quotient stream, selected limit, host equality,
countable choice row, or ambient completeness row. All exported data are already
contained in the certified finite $\mathsf{ProbeBundle}$ ledger, the displayed
$\Cont$ routes, the unary observation rows, the $\hsame$ transports, and the
shared $\Pkg$ provenance.
\end{theorem}
\begin{proof}
Start with the three-way cover of
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}. It identifies the
accepted $\StreamNameUp$ window, the pointwise $\RegSeqRat$ seal package, and
the $\RealUp$ endpoint read on the same unary observations, finite transport
ledger, endpoint transports, and provenance rows.

The first factor is the StreamName finite-window classifier. By
\autoref{thm:streamname-regseqrat-scheduled-seal-exhaustion}, the scheduled
seal over the accepted window is exhausted by the visible StreamName carrier and
classifier observations together with the finite ledger rows. Thus the
tail-selector source read begins at the finite-window classifier rather than at
a quotient stream or host-index equality.

The second factor is the RegSeqRat scheduled projection and readback row. Apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}: every public
row consumed by the $\RegSeqRat$ carrier is already one of the certified
pointwise rows, $\Cont$ routes, $\hsame$ transports, and $\Pkg$ provenance rows.
The scheduled projection therefore reads back exactly the finite window selected
by the StreamName classifier.

The third factor is the RealUp finite-prefix classifier. Use
\autoref{thm:streamname-regseqrat-finite-window-cover-determinacy} to compare
all finite windows selected by the tail read. Since the overlaps are already
compatible in the triple cover, the endpoint classifier depends only on the
finite prefix ledger presented by the RegSeqRat readback row. This gives the
claimed three-row factorization and excludes quotient, selected-limit,
countable-choice, host-equality, and ambient-completeness exports.
\end{proof}

\begin{theorem}[StreamName RegSeqRat tail-budget uniformity]
\label{thm:streamname-regseqrat-tail-budget-uniformity}
Let a finite accepted $\StreamNameUp$--$\RegSeqRat$ handoff packet present
StreamName finite observations through a common pointwise classifier, with
matching $\BHist$ rows, $\hsame$ transports, finite $\Cont$ routes, shared
$\Pkg$ provenance, and a displayed $\NameCert$ for the handoff surface. Suppose
the $\RegSeqRat$ tail selector carries a dyadic budget row consumed by the
finite-prefix $\RealUp$ endpoint. Then every later finite window accepted by
the same StreamName pointwise classifier factors through the same tail-budget
certificate.

Equivalently, once the packet has fixed the StreamName finite observations,
the RegSeqRat tail selector, and the RealUp budget consumer, enlarging the
finite window changes only the visible window ledger. It does not export a new
tail selector, budget witness, completion datum, quotient stream, host equality,
or ambient regularity row outside the certified $\NameCert$, $\Cont$, $\hsame$,
$\BHist$, and $\Pkg$ surface.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-realup-tail-selector-factorization}. The
tail-selector read factors through the StreamName finite-window classifier,
the RegSeqRat scheduled projection and readback row, and the RealUp
finite-prefix classifier. Thus the budget row is already located on the
displayed finite ledger rather than on a selected completion representative.

Next use
\autoref{thm:streamname-regseqrat-nested-window-seal-determinacy} for a later
finite window accepted by the same pointwise StreamName classifier. The nested
window has the same $\BHist$ source rows, $\hsame$ transport witnesses, finite
$\Cont$ routes, and $\Pkg$ provenance on the overlap, so the RegSeqRat
scheduled projection reads the same tail-selector certificate on the shared
part.

Finally compare all later windows with
\autoref{thm:streamname-regseqrat-finite-window-cover-determinacy}. The finite
cover determinacy theorem pastes the overlapping StreamName, RegSeqRat, and
RealUp rows into one cover-indexed source surface. Therefore each RealUp
budget consumer sees the same dyadic tail-budget certificate, and no further
completion, quotient, host-index, or off-ledger regularity datum can enter the
handoff.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp cover tail-budget finality]
\label{thm:streamname-regseqrat-realup-cover-tail-budget-finality}
Let $\{W_i\}_{i\in I}$ be a finite public $\StreamNameUp$ cover feeding the
same $\RegSeqRat$ finite-window consumer and the same finite-window $\RealUp$
endpoint. Suppose every displayed pairwise overlap satisfies the
nested-window handoff hypotheses, every nested pair satisfies the
nested-window seal determinacy hypotheses, and every triple overlap is
compatible in the triple seal cover. Then the cover forces a single
tail-budget certificate for the $\RegSeqRat$ consumer, and every endpoint read
factors through exactly the $\StreamNameUp$ finite-window classifier row, the
$\RegSeqRat$ scheduled projection and readback row, and the $\RealUp$
finite-prefix classifier row.

The forced certificate is a finite-cover surface over the displayed
$\NameCert$, $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\BHist$, $\Cont$,
$\hsame$, and $\Pkg$ rows. It contains no quotient stream data, selected limit,
host index equality, countable choice row, or ambient $\RealUp$ completeness
row.
\end{theorem}
\begin{proof}
First identify the source rows on pairwise overlaps. Apply
\autoref{thm:streamname-regseqrat-nested-window-handoff} to each displayed
nested overlap in the finite cover. The direct and two-step restrictions expose
the same StreamName classifier rows, unary observations, finite bundle ledger,
membership rows, and $\hsame$ comparisons.

Next transport those source rows through the endpoint seal. Use
\autoref{thm:streamname-regseqrat-nested-window-seal-determinacy} on the same
nested overlaps, and then apply
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover} on every displayed
triple. The RegSeqRat seal rows and the RealUp endpoint rows are therefore read
from the same finite transport, provenance, and pointwise observation surface
throughout the cover.

Now factor each endpoint read. By
\autoref{thm:streamname-regseqrat-realup-tail-selector-factorization}, every
accepted read passes through exactly the StreamName finite-window classifier,
the RegSeqRat scheduled projection and readback row, and the RealUp
finite-prefix classifier row. The factorization clauses rule out quotient
stream data, selected limits, host index equality, countable choice, and
ambient Real completeness as exported rows.

Finally apply
\autoref{thm:streamname-regseqrat-tail-budget-uniformity} to the cover-indexed
family of accepted windows. Since all overlaps have the same pointwise
classifier, $\BHist$ rows, $\hsame$ transports, finite $\Cont$ routes, shared
$\Pkg$ provenance, and displayed $\NameCert$ surface, the RegSeqRat tail
selector carries one dyadic budget certificate across the finite cover. Thus
the endpoint reads are forced by the same finite-cover surface and by exactly
the three classifier/projection rows named above.
\end{proof}
