\section{StreamName Real-RegSeq window source exhaustion}
\label{sec:streamname-real-regseq-window-source-exhaustion}

\begin{theorem}[StreamName Real-RegSeq finite-window source exhaustion]
\label{thm:streamname-real-regseq-window-source-exhaustion}
Every finite-window $\RegSeqRat$ consumer read or finite-window $\RealUp$
consumer read whose input is a public $\StreamNameUp$ packet factors through
exactly the public StreamName-RegSeqRat-RealUp source rows already exposed at
the handoff boundary. The source inventory consists of the selected
$\mathsf{RatHistoryClassifier}$ rows, the finite $\mathsf{ProbeBundle}$ row,
the corresponding $\mathsf{InBundle}$ membership rows, the
$\mathsf{UnaryHistory}$ observation rows, the visible $\hsame$ transports, the
finite $\Cont$ ledger, the shared $\Pkg$ provenance rows, the accepted
$\mathsf{DyadicRatCore}$ ledger entries, the accepted $\RegSeqRat$ pointwise
seal rows, and the $\RealUp$ endpoint seal row.

The factorization exports no quotient representative, no completion object, no
host index equality, no off-ledger regularity row, no Classical datum, and no
standard-bridge datum. Thus any finite public consumer read of the
StreamName-RegSeqRat-RealUp handoff is exhausted by the displayed finite-window
source inventory.
\end{theorem}
\begin{proof}
First separate the three obligation sources. By
\autoref{thm:streamname-real-regseq-obligation-separation}, StreamName
contributes only the carrier, selected rational-history classifier,
finite-bundle, membership, unary-observation, finite ledger, and public package
support rows, while RegSeqRat and RealUp supply their own seal-side
obligations.

Next pass from a single window to any certified finite cover. Apply
\autoref{thm:streamname-regseqrat-finite-window-cover-refinement-exhaustion}.
It says that cover refinement preserves exactly the displayed StreamName rows,
bundle-membership rows, unary observations, $\hsame$ transports, finite $\Cont$
entries, accepted $\mathsf{DyadicRatCore}$ entries, $\Pkg$ provenance rows,
accepted $\RegSeqRat$ pointwise seal rows, and the $\RealUp$ endpoint seal row.

Now identify the RegSeqRat read. Use
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. The pointwise
handoff consumes the accepted RegSeqRat seal rows through the same finite
StreamName packet, so no off-ledger regularity row or hidden host-index
equality can be introduced by the consumer read.

Finally identify the RealUp read. By
\autoref{thm:streamname-realup-seal-boundary}, the endpoint seal is fixed by
the accepted RegSeqRat rows and the visible finite StreamName ledger. Since the
preceding steps already exhaust the StreamName and RegSeqRat source rows, the
RealUp endpoint cannot reopen quotient representatives, completion objects,
Classical data, or standard-bridge data.
\end{proof}

\begin{theorem}[Real L10 terminal source pullback uniqueness]
\label{thm:real-l10-terminal-source-pullback-uniqueness}
Let $R_0$ and $R_1$ be terminal $\RealUp$ seal reads whose visible route is the
four-face L10 chain
$\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$. Suppose the
two reads preserve the same displayed $\StreamNameUp$ finite window, the same
$\DyadicRatCoreUp$ tolerance row, the same $\RegSeqRatUp$ readback and
regularity rows, the same componentwise $\hsame$ transports, the same finite
$\Cont$ ledger, the same $\Pkg$ provenance rows, and the same local
$\NameCert_{\StreamNameUp}$, $\NameCert_{\DyadicRatCoreUp}$,
$\NameCert_{\RegSeqRatUp}$, and $\NameCert_{\RealUp}$ support rows.

Then $R_0$ and $R_1$ determine the same terminal finite source pullback over the
displayed L10 route. The pullback is the finite $\mathsf{BHist}$ packet whose
four faces are the dyadic tolerance ledger, the StreamName finite-window
surface, the RegSeqRat readback and regularity surface, and the terminal RealUp
seal row. No quotient stream equality, host real equality, selected limit,
ambient completeness datum, countable-choice datum, metric-completeness datum,
or standard-bridge row is exported by this uniqueness claim.
\end{theorem}
\begin{proof}
First exhaust the source rows available to each terminal read. Apply
\autoref{thm:streamname-real-regseq-window-source-exhaustion}. Each read can
consume only the displayed finite StreamName window, the accepted
DyadicRatCore ledger entries, the RegSeqRat pointwise seal and regularity rows,
the visible $\hsame$ transports, $\Cont$ rows, $\Pkg$ provenance, and local
NameCert support.

Next identify the StreamName-to-RegSeqRat face. Use
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion}. Since the two
reads expose the same finite window and the same componentwise transports, the
RegSeqRat face is read from the same public StreamName packet rather than from
a host stream equality or a hidden representative.

Now identify the seal-facing RealUp face. Apply
\autoref{thm:regseqrat-tail-selector-real-seal-exhaustion} and
\autoref{thm:real-finite-window-seal-exhaustion}. These theorems place the
terminal readback on the same finite RegSeqRat tail-selector route and the same
RealUp finite-window seal, so no selected limit, ambient completeness datum,
countable-choice datum, or metric-completeness datum remains as a separate
source coordinate.

Finally repack the four displayed faces into one finite pullback. The
StreamName seal boundary fixes the finite window, the RegSeqRat boundary fixes
the readback and regularity rows, and the RealUp seal boundary fixes the
endpoint seal row. Because $R_0$ and $R_1$ preserve the same rows on every face,
the resulting finite $\mathsf{BHist}$ pullback is componentwise identical, and
there is no standard-bridge row available to distinguish a second terminal
source.
\end{proof}
