\section{StreamName RegSeqRat Real Lattice Dependency}
\label{sec:streamname-regseqrat-real-lattice-dependency}

The $\StreamNameUp$ finite-window packet is not an isolated kernel float. Its consumer route is the $\RegSeqRatUp$ readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ observation ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the $\RealUp$ seal surface of \autoref{ch:concrete-instances-real-namecert}; the lattice edge is carried through the child route below rather than by the hub file.

\begin{theorem}[StreamName RegSeqRat Real lattice dependency]
\label{thm:streamname-regseqrat-real-lattice-dependency}
Every accepted $\StreamNameUp$ finite-window packet consumed by $\RegSeqRatUp$ and then by $\RealUp$ factors through the same visible sibling route. The route begins with the StreamName finite-window rows, passes through the $\RegSeqRatUp$ readback rows of \autoref{ch:concrete-instances-regseqrat-namecert}, and ends at the $\RealUp$ seal rows of \autoref{ch:concrete-instances-real-namecert}. Along the entire route the only shared carrier coordinates are the displayed $\BHist$ observations, the componentwise $\hsame$ transports, the finite $\Cont$ continuation rows, the $\Pkg$ provenance rows, and the local $\NameCert$ rows naming the consumed packets.

The dependency exports no quotient stream, no host real equality, no selected limit, and no ambient completeness principle. In particular, the $\RealUp$ seal is read only as the downstream seal surface reached through the accepted finite StreamName and RegSeqRat packets.
\end{theorem}
\begin{proof}
Start with the StreamName finite-window surface. By \autoref{thm:streamname-finite-window-real-handoff-coverage}, the handoff exposes the finite observation window, the pointwise $\RegSeqRatUp$ rows, the $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

Next read the RegSeqRat sibling dependency. The pointwise handoff of \autoref{thm:streamname-regseqrat-pointwise-handoff} identifies the rows sent to $\RegSeqRatUp$ with the same StreamName carrier rows, finite-window classifier rows, certified unary observations, membership rows, and pointwise $\hsame$ comparisons. Thus the RegSeqRat readback surface of \autoref{ch:concrete-instances-regseqrat-namecert} is not a second carrier; it is the finite StreamName window read through the accepted pointwise packet.

Finally pass to the Real seal boundary. The factorization theorem \autoref{thm:streamname-real-seal-factorization-boundary} says that a finite-window $\RealUp$ seal read arising from the StreamName-to-RegSeqRat handoff factors through the StreamName point rows, accepted $\RegSeqRatUp$ seal rows, bundle and membership rows, unary observations, finite $\Cont$ ledger, displayed $\hsame$ transports, and $\Pkg$ provenance. This is exactly the seal-facing surface cited in \autoref{ch:concrete-instances-real-namecert}.

Coordinate exhaustion gives the exclusion clause. None of the cited finite-window, pointwise, or seal-factorization rows contains a quotient stream, host real equality witness, selected limit, or ambient completeness coordinate, so composing them cannot export one.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real dyadic-window pullback]
\label{thm:streamname-regseqrat-real-dyadic-window-pullback}
Every accepted $\StreamNameUp$ finite-window packet consumed by $\RegSeqRatUp$ and $\RealUp$ factors through the same finite pullback surface with four visible sibling rows: the StreamName finite-window row, the $\RegSeqRatUp$ readback row of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ observation ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the $\RealUp$ seal row of \autoref{ch:concrete-instances-real-namecert}. The pullback coordinates are only the displayed $\BHist$ observations, componentwise $\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows, and local $\NameCert$ rows already visible on those four sibling surfaces.

Consequently a downstream consumer of the packet may read the dyadic-window ledger as a common finite route from StreamName windows through RegSeqRat readback into the Real seal, but it obtains no quotient stream, no host real equality, no selected limit, and no ambient completeness principle.
\end{theorem}
\begin{proof}
First build the window surface. By \autoref{thm:streamname-finite-window-real-handoff-coverage}, the accepted finite-window handoff exposes the StreamName observation window together with the pointwise $\RegSeqRatUp$ rows, the $\RealUp$ seal boundary, componentwise $\hsame$ transport, finite $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

Next read the regular-rational side. The pointwise handoff theorem \autoref{thm:streamname-regseqrat-pointwise-handoff} identifies the $\RegSeqRatUp$ readback rows with the same StreamName carrier rows, finite-window classifier rows, certified unary observations, membership rows, and pointwise $\hsame$ comparisons. These are precisely the RegSeqRat rows named by \autoref{ch:concrete-instances-regseqrat-namecert}.

Now attach the dyadic ledger. The finite-window packet already exposes only visible observation rows before the RegSeqRat readback is consumed, and the dyadic observation surface of \autoref{ch:concrete-instances-dyadicratcore-namecert} supplies the endpoint and radius ledger through the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates. Thus the StreamName window, RegSeqRat readback, and dyadic ledger occupy one finite pullback surface rather than three independent carriers.

Finally pass to the Real seal. The boundary factorization of \autoref{thm:streamname-real-seal-factorization-boundary} says that the $\RealUp$ seal read arising from the StreamName-to-RegSeqRat handoff factors through the StreamName point rows, accepted $\RegSeqRatUp$ seal rows, bundle and membership rows, unary observations, finite $\Cont$ ledger, displayed $\hsame$ transports, and $\Pkg$ provenance. This is the Real-facing row cited in \autoref{ch:concrete-instances-real-namecert}.

Coordinate exhaustion proves the non-escape clause. The four sibling rows just composed contain no coordinate for a quotient stream, host real equality witness, selected limit, or ambient completeness operation, so the pullback route cannot export any of those objects to its downstream consumer.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real window source triangle]
\label{thm:streamname-regseqrat-real-window-source-triangle}
For every accepted finite $\StreamNameUp$ window consumed by a $\RegSeqRatUp$ row and then by a $\RealUp$ seal row, the StreamName window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ endpoint ledger, and the $\RealUp$ seal boundary form one finite pullback triangle of sources. Every route among the StreamName, RegSeqRat, and Real-facing surfaces factors through the same $\BHist$ packet, $\ProbeBundle$ and $\InBundle$ membership rows, $\mathsf{UnaryHistory}$ observations, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

The triangle exports no quotient stream equality, no host sequence equality, no selected limit, no metric-completeness witness, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
First expose the point source. By \autoref{thm:streamname-rat-regseqrat-lattice-source}, the accepted window is read through the StreamName row together with the rational and RegSeqRat point rows, bundle membership, unary observations, transport, continuation, provenance, and local naming coordinates.

Next use \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. It identifies the shared finite dyadic window on which the StreamName window row, RegSeqRat readback row, DyadicRatCore endpoint ledger, and Real seal boundary are all projected. Thus a route from any one of the three surfaces to another must pass through that same finite packet.

Finally apply the local non-escape clauses in this StreamName lattice section. The cited pullback and consumer-exhaustion rows list all available coordinates, and none is a quotient stream equality, host sequence equality, selected limit, metric-completeness witness, or ambient RealUp completeness principle. Hence the source triangle closes only the finite BEDC rows named in the statement.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real dyadic-pullback seal determinacy]
\label{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy}
Let two accepted $\StreamNameUp$ finite-window packets be consumed through the displayed $\BHist$ observations, componentwise $\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows, and local $\NameCert$ rows. If the two packets induce the same visible StreamName finite-window row, the same $\RegSeqRatUp$ readback row, the same $\DyadicRatCoreUp$ observation ledger, and the same $\RealUp$ seal row, then every $\RealUp$ seal consumer reads the same finite pullback surface.

In particular, the seal-facing read is determined by those four visible rows. No quotient stream, host real equality, selected limit, or ambient completeness datum can supply an alternate $\RealUp$ seal source for either packet.
\end{theorem}
\begin{proof}
First use \autoref{thm:streamname-regseqrat-real-lattice-dependency}. It identifies the visible sibling route from the accepted StreamName finite-window rows through the $\RegSeqRatUp$ readback rows and into the $\RealUp$ seal rows using only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next apply \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. Since the two packets have the same StreamName window row, RegSeqRat readback row, DyadicRatCore ledger, and Real seal row, the four-row finite pullback surface available to a downstream seal consumer is the same on both sides.

The Real seal route is pinned by \autoref{thm:streamname-real-seal-factorization-boundary}: any $\RealUp$ seal read arising from the StreamName-to-RegSeqRat handoff factors through the displayed finite-window rows, accepted RegSeqRat seal rows, bundle and membership rows, unary observations, finite $\Cont$ ledger, displayed $\hsame$ transports, and $\Pkg$ provenance. The RegSeqRat readback coordinate is the same coordinate described by \autoref{thm:streamname-regseqrat-pointwise-handoff}.

Thus every seal-facing consumer reaches one finite pullback surface. The cited rows contain no coordinate for quotient streams, host real equality witnesses, selected limits, or ambient completeness data, so none of those objects can act as a second source for the $\RealUp$ seal.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real dyadic-pullback consumer exhaustion]
\label{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}
Any downstream consumer citing the dyadic pullback route can project only the
StreamName finite-window row, the $\RegSeqRatUp$ readback row, the
$\DyadicRatCoreUp$ observation ledger, the $\RealUp$ seal row, and the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates on
those rows. It cannot extract a quotient stream, host real equality, selected
limit, or ambient completeness datum from the pullback.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. The
pullback route is exactly the four-row finite surface consisting of the
StreamName window, RegSeqRat readback, DyadicRatCore ledger, and Real seal,
with only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
coordinates attached.

Use \autoref{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy}.
The Real seal consumer is determined by those four rows, so any cited
pullback route must read the same finite surface rather than an external seal
source.

Exhaust the listed coordinates. None of the four sibling rows or boundary
coordinates contains a quotient stream, host real equality witness, selected
limit, or ambient completeness datum, and a downstream consumer cannot
recover data absent from the displayed pullback packet.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real terminal pullback exactness]
\label{thm:streamname-regseqrat-real-terminal-pullback-exactness}
Every terminal $\RealUp$ seal consumer of an accepted $\StreamNameUp$ finite-window packet factors through exactly the shared finite-window surface with four visible sibling rows: the StreamName finite-window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ observation ledger, and the $\RealUp$ seal row. The only shared coordinates available on that surface are the displayed $\BHist$ observations, componentwise $\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows, and local $\NameCert$ rows already attached to those four rows.

Consequently the terminal consumer has no alternate source through quotient streams, host real equality, selected limits, metric completeness, or ambient completeness. Its exact source is the displayed finite pullback packet.
\end{theorem}
\begin{proof}
First isolate the common surface. By \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}, the accepted finite-window packet is projected simultaneously to the StreamName finite-window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ observation ledger, and the $\RealUp$ seal row, with only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next pin the terminal seal read. Apply \autoref{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy}. Once those four visible rows agree, every $\RealUp$ seal consumer reads the same finite pullback surface rather than a second seal-facing source.

Finally exhaust the consumer interface by \autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}. A terminal consumer can project only the four rows and their displayed coordinates, so quotient streams, host real equality, selected limits, metric completeness, and ambient completeness have no coordinate from which an alternate source could be recovered.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real uniform pullback non-escape]
\label{thm:streamname-uniform-pullback-nonescape}
Let an accepted $\StreamNameUp$ finite-window packet be read through the
uniform finite-window seal and then consumed by a downstream $\RealUp$ seal
consumer. The consumer factors through the same four visible rows isolated in
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}: the
StreamName finite-window row, the $\RegSeqRatUp$ readback row, the
$\DyadicRatCoreUp$ observation ledger, and the $\RealUp$ seal row. Its only
shared coordinates are the displayed $\BHist$ observations, componentwise
$\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows,
and local $\NameCert$ rows attached to those four rows.

Consequently the uniform finite-window seal and the dyadic pullback present a
single finite BEDC carrier route to every such $\RealUp$ seal consumer. No
quotient stream, host real equality, selected limit, trichotomy row, or
ambient completeness datum is exported by that route.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. It
places the accepted StreamName packet behind the uniform finite-window seal
using the visible finite window, the displayed $\BHist$ observations,
componentwise $\hsame$ transport, finite $\Cont$ rows, $\Pkg$ provenance, and
local $\NameCert$ coordinates.

Next use \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. The
same sealed packet is read as the four-row pullback surface consisting of the
StreamName finite-window row, the $\RegSeqRatUp$ readback row, the
$\DyadicRatCoreUp$ observation ledger, and the $\RealUp$ seal row. Thus the
uniform seal does not create a route parallel to the dyadic pullback; it feeds
the same finite carrier surface.

Apply
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy} to
pin the downstream $\RealUp$ seal consumer to those four visible rows. Since
the seal-facing read is determined by the StreamName window, RegSeqRat
readback, DyadicRatCore ledger, and Real seal row, no second seal source can
enter through an external equality, limit, or completeness coordinate.

Finally apply
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}.
The consumer can project only the four rows and their displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates. The listed surface
has no quotient stream, host real equality, selected limit, trichotomy row,
or ambient completeness datum, so none of those objects escapes through the
uniform pullback route.
\end{proof}

\begin{theorem}[StreamName RegSeqRat Real route transitivity]
\label{thm:streamname-regseqrat-real-route-transitivity}
Every accepted $\StreamNameUp$ finite-window packet whose visible StreamName
row, $\DyadicRatCoreUp$ observation ledger, $\RegSeqRatUp$ readback row, and
$\RealUp$ seal row agree with the dyadic pullback route and with the uniform
finite-window seal route has a single composite $\RealUp$ seal consumer route.
That route has only the displayed $\BHist$ observations, componentwise
$\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows, and
local $\NameCert$ rows attached to those four sibling surfaces.

The composite route exports no quotient stream, no host real equality, no
selected limit, no trichotomy row, and no ambient completeness datum. Thus a
downstream $\RealUp$ seal consumer may cite one finite route from StreamName
windows through $\DyadicRatCoreUp$ and $\RegSeqRatUp$ rows into the $\RealUp$
seal, rather than separately choosing among the local handoff surfaces.
\end{theorem}
\begin{proof}
First identify the finite four-row surface. Apply
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. It places the
accepted StreamName packet, the dyadic observation ledger, the RegSeqRat
readback row, and the Real seal row on one pullback surface whose coordinates
are exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows.

Next compare the uniform seal with that surface. By
\autoref{thm:streamname-uniform-pullback-nonescape}, the uniform
finite-window seal feeds the same StreamName, DyadicRatCore, RegSeqRat, and
Real rows instead of producing a parallel consumer route. Hence the dyadic
pullback and the uniform seal name the same finite carrier path for the
downstream $\RealUp$ seal read.

Finally exhaust the consumer coordinates. Apply
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}.
A downstream consumer can project only the four displayed sibling rows and
their $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates. Since
those rows contain no quotient stream, host real equality, selected limit,
trichotomy row, or ambient completeness datum, no external coordinate can
escape through the composite seal route.
\end{proof}

\begin{theorem}[StreamName Real observation-budget factorization]
\label{thm:streamname-real-observation-budget-factorization}
Every accepted $\StreamNameUp$ finite-window packet consumed by a
$\RealObservationBudgetUp$ precision request factors through the same visible
route
$$
\StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp.
$$
The consumer may use only the displayed $\BHist$ observations, componentwise
$\hsame$ transports, finite $\Cont$ routes, $\Pkg$ provenance, and local
$\NameCert$ rows available on that route. The request supplies no quotient
stream, no host equality, no hidden limit selection, and no ambient
completeness coordinate.
\end{theorem}
\begin{proof}
Start with the finite StreamName packet. By
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}, the packet is
already read through the four visible sibling rows: StreamName finite window,
$\DyadicRatCoreUp$ observation ledger, $\RegSeqRatUp$ readback, and $\RealUp$
seal boundary.

Next attach the observation-budget consumer. The finite-route coverage theorem
\autoref{thm:real-observation-budget-finite-route-coverage} routes every
accepted $\RealObservationBudgetUp$ seal read through its precision request,
finite window family, dyadic readback rows, regular-sequence handoff rows, and
real seal rows. The consumer factorization theorem
\autoref{thm:real-observation-budget-regseq-real-consumer-factorization}
confines the $\RegSeqRatUp$ and $\RealUp$ reads to the same displayed
$\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ data.

Finally use
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}.
The StreamName handoff exposes only the four finite rows and their listed BEDC
coordinates, while the observation-budget theorems consume exactly those rows.
No cited surface carries a quotient stream, host equality, hidden limit
selection, or ambient completeness datum, so the precision request cannot
introduce one.
\end{proof}

\begin{theorem}[StreamName Real budget route determinacy]
\label{thm:streamname-real-budget-route-determinacy}
Let two accepted $\StreamNameUp$ finite-window packets induce the same visible
StreamName window row, the same $\DyadicRatCoreUp$ ledger row, the same
$\RegSeqRatUp$ readback row, the same $\RealUp$ seal row, and the same accepted
$\RealObservationBudgetUp$ precision-request route. Then every budget consumer
reads the same finite BEDC route through the displayed $\BHist$ observations,
componentwise $\hsame$ transports, finite $\Cont$ continuations, $\Pkg$
provenance, and local $\NameCert$ coordinates.

No quotient stream, host equality, selected limit, trichotomy row, or ambient
completeness datum can provide an alternate budget source for either packet.
\end{theorem}
\begin{proof}
First use
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}. The shared
visible StreamName window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ readback,
and $\RealUp$ seal row place both accepted packets on the same four-row
pullback surface.

Next attach the budget route. By
\autoref{thm:streamname-real-observation-budget-factorization}, any
$\RealObservationBudgetUp$ precision request consuming either packet factors
through that StreamName-to-dyadic-to-regular-sequence-to-real route. The
consumer route theorem
\autoref{thm:real-observation-budget-regseq-real-consumer-factorization}
confines the budget-facing $\RegSeqRatUp$ and $\RealUp$ reads to the displayed
$\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ coordinates.

Apply
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-seal-determinacy}. Since
the two packets agree on the four visible rows and on the accepted precision
request route, the downstream seal-facing consumer has no second row from which
to choose a different finite budget source.

Finally use consumer exhaustion for the pullback surface. The available
consumer projections are exactly the listed $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ coordinates, so quotient streams, host equalities,
selected limits, trichotomy rows, and ambient completeness data cannot enter as
alternate budget inputs.
\end{proof}

\begin{theorem}[StreamName observation-budget CauchyLimitSeal compatibility]
\label{thm:streamname-observation-budget-cauchy-limit-seal-compatibility}
Let an accepted $\StreamNameUp$ finite-window packet be read both by a
$\RealObservationBudgetUp$ precision request and by a $\CauchyLimitSealUp$
consumer. The two reads factor through the same visible four-row surface:
the StreamName finite window, the $\DyadicRatCoreUp$ observation ledger, the
$\RegSeqRatUp$ readback, and the $\RealUp$ seal row.

The common route may project only the displayed $\BHist$ observations,
componentwise $\hsame$ transports, finite $\Cont$ continuations, $\Pkg$
provenance, and local $\NameCert$ coordinates on that finite pullback. It
exports no quotient stream, host equality, selected limit, ambient
completeness, metric-completion row, or standard bridge row.
\end{theorem}
\begin{proof}
First read the precision-budget route. By
\autoref{thm:streamname-real-observation-budget-factorization}, every
$\RealObservationBudgetUp$ request consumes the accepted StreamName packet
through the displayed StreamName window, $\DyadicRatCoreUp$ ledger,
$\RegSeqRatUp$ readback, $\RealUp$ seal, and the visible $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next read the CauchyLimitSeal route. The forward lattice theorem
\autoref{thm:streamname-cauchy-limit-seal-forward-lattice} places the seal
consumer on the StreamName window, RegSeqRat readback, dyadic ledger, Real
seal row, and displayed finite-window seal surface. The reverse source
exhaustion theorem
\autoref{thm:streamname-cauchy-limit-seal-reverse-source-exhaustion} says that
no other public source row is available to that consumer.

Finally identify the two routes. Apply
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback} to read the
StreamName finite window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ readback,
and $\RealUp$ seal as one finite pullback surface. Then use
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}:
both consumers can project only the displayed $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ coordinates of that pullback. Since neither cited
route contains a quotient stream, host equality, selected limit, ambient
completeness, metric-completion row, or standard bridge row, the two
consumers cannot diverge into hidden completion routes.
\end{proof}

\begin{theorem}[StreamName Real RegSeqRat seal pullback exhaustion]
\label{thm:streamname-real-regseq-seal-pullback-exhaustion}
Every accepted $\RealUp$ seal pullback read routed through an accepted
$\StreamNameUp$ finite-window packet, the $\RegSeqRatUp$ classifier row, and
the $\RealUp$ seal factors through exactly the displayed rows of this route:
the StreamName finite-window row, the $\DyadicRatCoreUp$ observation ledger,
the $\RegSeqRatUp$ readback and classifier surface, the $\RealUp$ seal row,
and the attached $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
coordinates.

Thus the Real seal pullback route exports no quotient stream, no selected
limit, no host real equality, and no ambient completeness witness. A
downstream seal consumer receives only the same finite packet presented by
the StreamName finite window, the RegSeqRat row, and the Real seal boundary.
\end{theorem}
\begin{proof}
Start with the source lattice. By
\autoref{thm:streamname-regseqrat-real-lattice-dependency}, the accepted
StreamName-to-RegSeqRat-to-Real route is already confined to the visible
finite-window rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ coordinates. The theorem also records that the route has no
quotient stream, host real equality, selected limit, or ambient completeness
coordinate.

Next force the finite pullback route. Apply
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback} to read the
StreamName finite-window row, the $\DyadicRatCoreUp$ ledger, the
$\RegSeqRatUp$ readback row, and the $\RealUp$ seal row as one finite surface.
Then use
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}
to restrict every downstream consumer of that surface to the four displayed
rows and their listed BEDC coordinates.

Finally compare the seal consumer. The compatibility theorem
\autoref{thm:streamname-observation-budget-cauchy-limit-seal-compatibility}
identifies the observation-budget read and the $\CauchyLimitSealUp$ read on
the same finite pullback packet. Hence a Real seal pullback read routed
through StreamName, RegSeqRat, and Real cannot select another source: it
delivers precisely that finite packet to downstream seal consumers and no
hidden completion witness beyond it.
\end{proof}

\begin{theorem}[StreamName RealCompletionExactBoundary terminal pullback lock]
\label{thm:streamname-realcompletionexactboundary-terminal-pullback-lock}
Every accepted four-face $\StreamNameUp$--$\RegSeqRatUp$--$\DyadicRatCoreUp$--$\RealUp$ finite pullback consumed by a $\RealCompletionExactBoundaryUp$ packet factors through the exact terminal route
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
The StreamName window is read as $W$, the RegSeqRat readback as $R$, the DyadicRatCore ledger as $D$, and the Real seal as $E$ after the governing seal, classifier, witness-ledger, and budget rows $L,K,J,S$.

Conversely, the exact-boundary packet reads the same StreamName window, RegSeqRat readback, DyadicRatCore ledger, and RealUp seal as the four faces of the StreamName pullback. The lock exports no quotient stream, host sequence equality, selected limit, countable choice, ambient completeness, metric completeness, or bridge row.
\end{theorem}
\begin{proof}
First isolate the StreamName-side surface. By \autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}, the accepted finite-window packet exposes exactly the StreamName finite-window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ observation ledger, the $\RealUp$ seal row, and their displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next exhaust the seal read. Apply \autoref{thm:streamname-real-regseq-seal-pullback-exhaustion}: a Real seal pullback routed through StreamName, RegSeqRat, and Real delivers precisely that finite packet to downstream seal consumers and supplies no quotient stream, selected limit, host real equality, or ambient completeness witness.

Now read the completion boundary. The four-face exactness theorem \autoref{thm:real-completion-exact-boundary-four-face-exactness} says that an accepted $\RealCompletionExactBoundaryUp$ packet exposes the four Phase Real and Completion faces $W,R,D,E$ after the rows $L,K,J,S$ and before the structural rows $H,C,P,N$. The terminal-route theorem \autoref{thm:real-completion-exact-boundary-terminal-route-pullback} then pins the terminal $\RealUp(E)$ read to the same route $L,K,J,S,W,R,D,E,H,C,P,N$.

It remains to identify the two reads. The StreamName pullback names its four faces as the StreamName window, RegSeqRat readback, DyadicRatCore ledger, and RealUp seal; the exact-boundary packet names the same four faces as $W,R,D,E$. Since both cited routes expose only their displayed finite BEDC coordinates, there is no additional row on which the two reads could diverge.

The exclusion clause follows from the same inventories. Neither the StreamName pullback exhaustion nor the exact-boundary terminal route contains a quotient stream, host sequence equality, selected limit, countable-choice row, ambient-completeness row, metric-completeness row, or bridge row, so an accepted consumer of one surface cannot import any of those objects into the other.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp lattice budget cover]
\label{thm:streamname-regseqrat-realup-lattice-budget-cover}
Every accepted $\StreamNameUp$ finite-window packet used as a Phase Real and
Completion budget cover factors through exactly four sibling rows: the
StreamName finite-window row, the $\DyadicRatCoreUp$ observation ledger, the
$\RegSeqRatUp$ readback and classifier surface, and the $\RealUp$ seal row.
The cover exposes only the displayed $\BHist$ observations, componentwise
$\hsame$ transports, finite $\Cont$ continuations, $\Pkg$ provenance rows, and
local $\NameCert$ coordinates attached to those four rows.

Consequently the budget cover supplies a finite route from StreamName windows
through dyadic observation and regular-rational readback into the Real seal.
It exports no quotient stream, no host real equality, no selected limit, no
ambient completeness coordinate, no metric-completion row, and no standard
bridge row.
\end{theorem}
\begin{proof}
First isolate the four-row pullback. By
\autoref{thm:streamname-regseqrat-real-dyadic-window-pullback}, every accepted
finite-window packet consumed by $\RegSeqRatUp$ and $\RealUp$ is read through
the StreamName finite-window row, the $\DyadicRatCoreUp$ observation ledger,
the $\RegSeqRatUp$ readback row, and the $\RealUp$ seal row, with only the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.

Next exhaust the consumer projections. The theorem
\autoref{thm:streamname-regseqrat-real-dyadic-pullback-consumer-exhaustion}
says that any downstream consumer citing that dyadic pullback can project only
those four rows and their listed coordinates. Thus a budget cover cannot add a
second carrier surface while remaining a consumer of the accepted
finite-window packet.

Now attach the Phase Real budget route. By
\autoref{thm:streamname-real-observation-budget-factorization}, every
$\RealObservationBudgetUp$ precision request using the accepted packet factors
through the same route from $\StreamNameUp$ to $\DyadicRatCoreUp$ to
$\RegSeqRatUp$ to $\RealUp$. The request supplies no quotient stream, host
equality, hidden limit selection, or ambient completeness coordinate.

Finally pass to the Completion exit boundary. Apply
\autoref{thm:streamname-real-regseq-seal-pullback-exhaustion}: the Real seal
pullback read routed through StreamName, RegSeqRat, and Real delivers exactly
the same finite packet to downstream seal consumers. Since the preceding
factorization already lists all available $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ coordinates, there is no remaining coordinate from which a
metric-completion row or standard bridge row could be recovered.
\end{proof}
