\begin{theorem}[StreamName RegSeqRat triple-overlap source cocycle]
\label{thm:streamname-regseqrat-triple-overlap-source-cocycle}
Let $\mathcal{W}_0,\mathcal{W}_1,\mathcal{W}_2$ be certified finite
$\StreamNameUp$ windows. Suppose each pair carries a certified finite overlap,
the three pairwise restrictions agree on every certified unary observation,
selected $\mathsf{RatHistoryClassifier}$ row, $\mathsf{ProbeBundle}$ ledger
row, $\mathsf{InBundle}$ membership row, and displayed $\hsame$ row, and the
three overlaps have a certified common triple overlap $K_{012}$. Then the three
induced $\RegSeqRat$ handoff packages, and the three induced finite-window
$\RealUp$ handoff packages, determine one StreamName source surface on
$K_{012}$.

The triple source surface consists only of the restricted StreamName
finite-window rows on $K_{012}$. It excludes completion data, quotient data,
host index equality, every $\RegSeqRat$ regularity row, every $\RealUp$ seal
classifier row, and every $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
First restrict the three windows to the common triple overlap $K_{012}$. Each
restricted pair is a certified finite overlap with the same displayed unary
observations, classifier rows, bundle rows, membership rows, and $\hsame$
comparisons.

Apply \autoref{thm:streamname-real-regseq-overlap-unique-source} to
$(\mathcal{W}_0,\mathcal{W}_1)$ on $K_{012}$ and again to
$(\mathcal{W}_1,\mathcal{W}_2)$ on $K_{012}$. The first application identifies
the source surface of $\mathcal{W}_0$ with that of $\mathcal{W}_1$; the second
identifies the source surface of $\mathcal{W}_1$ with that of
$\mathcal{W}_2$.

The displayed $\hsame$ rows compose through the common middle restriction, so
the two identifications give a single source surface for all three windows on
the triple overlap. The optional third pair
$(\mathcal{W}_0,\mathcal{W}_2)$ reads the same restricted rows and therefore
lands on that same surface.

Finally use the exclusion clause in
\autoref{thm:streamname-real-regseq-overlap-unique-source}. The cocycle is a
statement about the public StreamName finite-window source only; no completion,
quotient, host-index, RegSeqRat regularity, RealUp seal, or RealUp completeness
row is part of the source surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat triple-overlap seal cocycle]
\label{thm:streamname-regseqrat-triple-overlap-seal-cocycle}
Let $\mathcal{W}_0,\mathcal{W}_1,\mathcal{W}_2$ be certified finite
$\StreamNameUp$ windows with pairwise certified overlaps and a certified common
triple overlap $K_{012}$. Suppose the source hypotheses of
\autoref{thm:streamname-regseqrat-triple-overlap-source-cocycle} hold, and
suppose the three induced $\RegSeqRat$ handoff packages consume one shared
$\DyadicRatCoreUp$ finite ledger on every restriction to $K_{012}$. Then the
$\RealUp$ seal classifier rows induced from the three handoffs agree on
$K_{012}$.

This agreement is only the finite-window seal row agreement produced from the
shared StreamName source and shared DyadicRatCore ledger. It does not include
completion data, quotient data, host index equality, or a $\RealUp$
completeness row.
\end{theorem}
\begin{proof}
First fix the source. By
\autoref{thm:streamname-regseqrat-triple-overlap-source-cocycle}, the three
windows expose one StreamName source surface on $K_{012}$ for their induced
RegSeqRat and finite-window RealUp handoffs.

Next compare the first two seal rows. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} to
$(\mathcal{W}_0,\mathcal{W}_1)$ after restricting to $K_{012}$. The source rows
are the common rows just fixed, and the DyadicRatCore finite ledger is shared by
hypothesis, so the induced RealUp seal classifier rows agree pointwise there.

Compare the second and third seal rows in the same way. The pair
$(\mathcal{W}_1,\mathcal{W}_2)$ has the same restricted source and the same
consumed dyadic ledger, so pointwise seal stability identifies their induced
classifier rows on $K_{012}$.

These two pointwise agreements have the same middle classifier row. Hence the
three induced RealUp seal classifier rows form one row on the triple overlap.
The construction never asks for completion, quotient, host-index, or RealUp
completeness data, because pointwise seal stability only reads the finite
StreamName source and the shared dyadic ledger.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-cover pasted source exhaustion]
\label{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion}
Let $\{\mathcal{W}_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows. Suppose every pair has a certified finite overlap,
all pairwise restrictions agree on the displayed StreamName source rows, every
triple overlap satisfies the source and seal cocycle hypotheses above, and all
induced $\RegSeqRat$ handoff packages consume the same DyadicRatCore finite
ledger on their displayed overlaps. Then the family pastes to one
$\RegSeqRat$ and finite-window $\RealUp$ source surface over the finite union
of the windows.

The pasted surface is exhausted by the public StreamName finite-window rows,
the displayed $\hsame$ comparisons, and the shared DyadicRatCore ledger rows.
It has no completion data, quotient data, host index equality, or $\RealUp$
completeness row.
\end{theorem}
\begin{proof}
Proceed by finite $\mathsf{ProbeBundle}$ induction over the cover inventory.
The empty inventory has no exposed source row, and the singleton inventory is
the certified source surface of its one StreamName window.

For the induction step, assume a finite subcover has already pasted to one
RegSeqRat and finite-window RealUp source surface. Let $\mathcal{W}_j$ be the
next certified window. On each overlap between $\mathcal{W}_j$ and a member of
the subcover, apply
\autoref{thm:streamname-real-regseq-overlap-unique-source} to obtain the same
source rows, and apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} to stabilize the
induced RealUp seal classifier rows over the shared dyadic ledger.

Now paste the new window to the existing subcover surface. Use
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting} on each displayed
overlap, and use
\autoref{thm:streamname-regseqrat-pasted-seal-associativity} to see that the
order of adjoining the finitely many overlap rows does not change the pasted
classifier surface.

The triple-overlap source and seal cocycles supply the compatibility needed
when two old windows and the new window meet. They identify the common source
and seal rows on each triple intersection, so no additional choice of a source
or classifier row is introduced by the induction step.

Finally exhaust the pasted finite union. Every row inserted during the
induction is either a public StreamName finite-window row, a displayed
$\hsame$ comparison, or a shared DyadicRatCore ledger row used by the RegSeqRat
handoff. Completion data, quotient data, host index equality, and RealUp
completeness rows have no carrier coordinate in this finite pasted source.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-cover pasted seal exhaustion]
\label{thm:streamname-regseqrat-finite-cover-pasted-seal-exhaustion}
Let $\{\mathcal{W}_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows satisfying the source hypotheses of
\autoref{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion}.
Assume moreover that every triple overlap satisfies
\autoref{thm:streamname-regseqrat-triple-overlap-seal-cocycle}, and that all
displayed overlaps consume one shared $\DyadicRatCoreUp$ ledger in the
induced $\RegSeqRat$ handoff packages. Then the induced finite-window
$\RealUp$ seal classifier rows paste to one seal surface over the finite union
of the windows.

The pasted seal surface is exhausted by the finite-window RealUp classifier
rows forced by the common StreamName source and the shared DyadicRatCore
ledger. It excludes completion data, quotient data, host index equality,
selected limits, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First fix the source surface. Apply
\autoref{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion} to
the family of windows. This gives one RegSeqRat and finite-window RealUp
source surface over the finite union, with no completion, quotient,
host-index, or completeness coordinate.

We now attach seal rows by finite $\mathsf{ProbeBundle}$ induction over the
cover inventory. The empty inventory has no classifier row to paste, and the
singleton inventory carries the seal row induced from its certified StreamName
window and shared DyadicRatCore ledger.

For the induction step, assume a finite subcover already carries one pasted
seal surface. Let $\mathcal{W}_j$ be the next certified window. On each
displayed overlap with the existing subcover, apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability}; the source row is
the fixed source surface, and the dyadic ledger is the shared ledger from the
hypotheses.

Use \autoref{thm:streamname-regseqrat-pointwise-seal-pasting} to attach the
seal row of $\mathcal{W}_j$ along those overlap rows. When two old windows and
$\mathcal{W}_j$ meet, the triple-overlap seal cocycle identifies the three
restricted classifier rows, so the attachment does not depend on which overlap
is read first.

Finally apply
\autoref{thm:streamname-regseqrat-pasted-seal-associativity}. The associativity
of pasted seal rows, together with the triple-overlap seal cocycle, makes the
finite $\mathsf{ProbeBundle}$ induction order-independent. Thus all induced
finite-window RealUp seal classifier rows determine one seal surface over the
finite union.

Every coordinate used in the construction is a finite-window classifier row
obtained from the common StreamName source and the shared DyadicRatCore
ledger. Completion data, quotient data, host index equality, selected limits,
and RealUp completeness are not introduced by pointwise seal stability,
pointwise seal pasting, or pasted seal associativity.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-cover pasted seal terminality]
\label{thm:streamname-regseqrat-finite-cover-pasted-seal-terminality}
Let $\{\mathcal{W}_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows satisfying the hypotheses of
\autoref{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion}.
Assume every triple overlap satisfies
\autoref{thm:streamname-regseqrat-triple-overlap-seal-cocycle}, and assume all
displayed overlaps consume one shared $\DyadicRatCoreUp$ ledger in the induced
$\RegSeqRat$ handoff packages. If $\mathcal{S}$ and $\mathcal{S}'$ are two
induced finite-window $\RealUp$ pasted seal surfaces over the finite union with
the same displayed $\StreamNameUp$ window rows, $\DyadicRatCoreUp$ ledger rows,
$\RegSeqRat$ handoff rows, overlap $\hsame$ data, and displayed $\BHist$,
$\Cont$, $\Pkg$, and $\NameCert$ support rows, then $\mathcal{S}=\mathcal{S}'$
as pasted seal surfaces over the finite union.

This terminality is a finite L10 seal statement. It contains no completion
data, quotient data, host index equality, selected limits, countable choice, or
$\RealUp$ completeness.
\end{theorem}
\begin{proof}
First fix the source side. By
\autoref{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion}, the
displayed StreamName rows, overlap $\hsame$ data, and shared
DyadicRatCore ledger rows determine one RegSeqRat and finite-window RealUp
source surface over the finite union. Thus $\mathcal{S}$ and $\mathcal{S}'$
are compared over the same finite source surface.

Next apply
\autoref{thm:streamname-regseqrat-finite-cover-pasted-seal-exhaustion} to both
candidate pasted seal surfaces. Each candidate is exhausted by the same
finite-window RealUp classifier rows forced by that source surface and the
same shared DyadicRatCore ledger. The displayed RegSeqRat handoff rows and
$\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ support rows therefore leave no
separate seal coordinate that could distinguish the two candidates.

It remains to identify the overlap choices used in the finite pasting. On each
displayed pairwise overlap,
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} gives the same
pointwise seal row for both candidates, because the source row and dyadic
ledger row are the same. The triple-overlap compatibility is exactly
\autoref{thm:streamname-regseqrat-triple-overlap-seal-cocycle}, so the
pointwise overlap rows agree on every common triple restriction.

Finally use \autoref{thm:streamname-regseqrat-pointwise-seal-pasting} and
\autoref{thm:streamname-regseqrat-pasted-seal-associativity}. Pointwise
pasting attaches the same local seal rows along the same overlap data, and
associativity makes the finite attachment order irrelevant. Hence both
$\mathcal{S}$ and $\mathcal{S}'$ are the same pasted finite-window RealUp seal
surface over the finite union.

The argument only reads finite StreamName rows, DyadicRatCore ledger rows,
RegSeqRat handoff rows, overlap $\hsame$ data, and displayed support rows.
Completion data, quotient data, host index equality, selected limits,
countable choice, and RealUp completeness are not carrier coordinates in this
terminal pasted seal surface.
\end{proof}
