\section{StreamName RegSeqRat Pointwise Handoff}
\label{sec:streamname-regseqrat-pointwise-handoff}

\begin{theorem}[StreamName pointwise handoff package]
\label{thm:streamname-regseqrat-pointwise-handoff}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be a finite observation bundle. A
pointwise handoff from $\StreamNameUp$ to $\RegSeqRat$ or to a finite-window
$\RealUp$ consumer consists exactly of the following source rows:
\begin{enumerate}
  \item $\mathsf{RatStreamNameCarrier}(s)$ and
  $\mathsf{RatStreamNameCarrier}(t)$;
  \item $\mathsf{RatStreamNameClassifier}(s,t)$, restricted on
  $\mathcal{P}$ through
  $\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})$;
  \item for each certified $n$, the rows
  $\mathsf{UnaryHistory}(n)$, $\mathsf{InBundle}(n,\mathcal{P})$, and the
  pointwise $\hsame$ comparison carried by the classifier at $n$.
\end{enumerate}
Every row handed to $\RegSeqRat$ or to a finite-window $\RealUp$ consumer is
one of these pointwise StreamName rows. The handoff contains no completion
object, quotient row, host-index equality, $\RegSeqRat$ regularity row, or
$\RealUp$ seal classifier.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.StreamNameRegSeqRatPointwiseHandoff}
\begin{proof}
Project the public finite-window StreamName surface by
\autoref{thm:streamname-real-regseq-finite-window-handoff}. It exposes the
selected classifier rows, the finite $\mathsf{ProbeBundle}$ ledger,
$\mathsf{InBundle}$ membership, and $\mathsf{UnaryHistory}$ observations.

Now read the selected classifier pointwise. Definitions
\autoref{def:rat-stream-name-carrier} and
\autoref{def:rat-stream-name-classifier} identify the carrier and classifier
rows as statements about the observations $s(n)$ and $t(n)$ at certified unary
histories. The finite-window classifier row restricts exactly those
pointwise observations to the selected bundle.

Finally apply
\autoref{thm:streamname-regseqrat-pointwise-handoff-exhaustion} and
\autoref{thm:streamname-real-regseq-obligation-separation}. These theorems
repack the pointwise rows into the same downstream handoff and keep
regularity and seal classifiers on the consumer side.
\end{proof}

\begin{theorem}[StreamName RegSeqRat observation stability]
\label{thm:streamname-regseqrat-observation-stability}
Let $s,t,u,s',t':\mathsf{BHist}\to\mathsf{BHist}$ and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be finite. Suppose
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal{P})$ and
$\mathsf{RatStreamNameFiniteWindowClassifier}(t,u,\mathcal{P})$ hold, and
suppose every certified $n$ with
$\mathsf{InBundle}(n,\mathcal{P})$ and $\mathsf{UnaryHistory}(n)$ carries the
pointwise comparisons $\hsame(s(n),s'(n))$ and $\hsame(t(n),t'(n))$. Then the
same bundle also supports the self, symmetric, transitive, and transported
pointwise classifier rows:
$$
\begin{gathered}
\mathsf{RatStreamNameFiniteWindowClassifier}(s,s,\mathcal{P}),\\
\mathsf{RatStreamNameFiniteWindowClassifier}(t,s,\mathcal{P}),\\
\mathsf{RatStreamNameFiniteWindowClassifier}(s,u,\mathcal{P}),\\
\mathsf{RatStreamNameFiniteWindowClassifier}(s',t',\mathcal{P}).
\end{gathered}
$$
Thus a $\RegSeqRat$ handoff or finite-window $\RealUp$ consumer may transport
the StreamName observation window only along pointwise $\hsame$ rows already
certified in the finite bundle.
\end{theorem}
\begin{proof}
Unfold the finite-window classifier at a certified member of
$\mathcal{P}$. The hypotheses provide the pointwise classifier rows
$s(n)\sim t(n)$ and $t(n)\sim u(n)$ together with the carrier row for $s(n)$.

Apply the finite-window stability fields represented on the Lean side by
$\mathsf{RatStreamNameFiniteWindowClassifier\_stability\_fields}$. Its four
projections give the self row for $s$, the symmetric row from $t$ to $s$, the
transitive row from $s$ to $u$, and the transported row from $s'$ to $t'$ on
the same finite bundle.

The consumer boundary is unchanged. By
\autoref{thm:streamname-regseqrat-pointwise-handoff}, the transported rows are
still only pointwise StreamName observations plus bundle membership and unary
history evidence, so no downstream regularity or seal row is imported.
\end{proof}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_stability\_fields}

\begin{theorem}[StreamName RealUp constant observation handoff]
\label{thm:streamname-realup-constant-observation-handoff}
Let $d,e:\mathsf{BHist}$ be rational-history endpoints, let
$r,q:\mathsf{BHist}\to\mathsf{BHist}$ be observation schedules, and let
$\mathcal{P}:\mathsf{ProbeBundle}$ be a finite unary observation bundle. The
constant StreamName rows
$$
n\mapsto \mathsf{RatStreamName\_constant}(d,r(n)),
\qquad
n\mapsto \mathsf{RatStreamName\_constant}(e,q(n))
$$
feed $\RegSeqRat$ and finite-window $\RealUp$ only through the pointwise rows
of \autoref{thm:streamname-regseqrat-pointwise-handoff}. The rational endpoint
classifier for $d$ and $e$ supplies the constant point observations, while
regularity, dyadic seal data, and the $\RealUp$ seal classifier remain
downstream obligations.
\end{theorem}
\begin{proof}
Start from the constant StreamName boundary. Apply
\autoref{thm:streamname-real-regseq-constant-boundary}: a constant finite
window exports the rational point-classifier row, the finite bundle ledger,
membership rows, and unary observation rows, while $\RegSeqRat$ regularity
remains outside the StreamName source.

Apply
\autoref{thm:streamname-constant-scheduled-observation-exactness} to the two
scheduled constant rows. The Lean definitions
$\mathsf{RatStreamNameCarrier}$, $\mathsf{RatStreamNameClassifier}$, and
$\mathsf{RatStreamName\_constant}$ express this as pointwise observations of
the fixed rational endpoints $d$ and $e$ at every certified unary history.

Finally pass the resulting finite window through
\autoref{thm:realup-finite-window-exhaustion-obligation} and
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. These RealUp
consumer theorems read only the pointwise StreamName packet and its ledger, so
the constant handoff contributes no completion, quotient, host-index equality,
regularity witness, or seal classifier.
\end{proof}

\begin{theorem}[StreamName singleton diagonal handoff]
\label{thm:streamname-regseqrat-singleton-diagonal-handoff}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$n:\mathsf{BHist}$ be a certified unary observation, and let $S_n$ be the
singleton probe bundle generated by $n$. If
$\mathsf{RatStreamNameClassifier}(s,t)$ and $\mathsf{UnaryHistory}(n)$ hold,
then the exact finite-window packet handed to $\RegSeqRat$ or to a
finite-window $\RealUp$ consumer is
$$
\begin{gathered}
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,S_n),\\
\mathsf{InBundle}(n,S_n),\\
\mathsf{RatHistoryClassifier}(s(n),t(n)).
\end{gathered}
$$
This singleton packet exports no $\RegSeqRat$ regularity row, no $\RealUp$
seal classifier, no completion object, and no quotient row.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_singleton\_diagonal\_handoff}
\begin{proof}
Start from the global StreamName classifier. By
\autoref{def:rat-stream-name-classifier}, reading it at the certified unary
history $n$ gives the pointwise rational-history classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

Now restrict the classifier to the singleton bundle $S_n$. The finite-window
definition, equivalently
\autoref{thm:rat-stream-name-finite-window-exhausts-classifier}, says that
the only visible observation slot of $S_n$ is the row selected by
$\mathsf{InBundle}(n,S_n)$. Hence the restricted row is exactly
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,S_n)$ together with that
membership witness and the pointwise classifier at $n$.

Finally read the packet through
\autoref{thm:streamname-regseqrat-pointwise-handoff}. The consumer boundary is
the one separated in
\autoref{thm:streamname-real-regseq-obligation-separation}: regularity,
sealing, completion, and quotient data remain downstream, so the singleton
source row is precisely the finite-window packet displayed above.
\end{proof}

\begin{theorem}[StreamName singleton restriction handoff exactness]
\label{thm:streamname-singleton-restriction-handoff-exactness}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$n:\mathsf{BHist}$ be a certified unary observation, and let $S_n$ be the
singleton probe bundle generated by $n$. For any certified restriction of a
finite observation bundle through $S_n$, the restricted $\RegSeqRat$ and
finite-window $\RealUp$ handoff is exactly the tuple
$$
\begin{gathered}
\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,S_n),\\
\mathsf{InBundle}(n,S_n),\\
\mathsf{UnaryHistory}(n),\\
\mathsf{RatHistoryClassifier}(s(n),t(n)).
\end{gathered}
$$
It exports no $\RegSeqRat$ regularity row, $\RealUp$ seal classifier,
completion object, quotient row, or host-index equality.
\end{theorem}
\begin{proof}
Begin with the singleton diagonal handoff of
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff}. It identifies
the singleton source packet with the finite-window classifier over $S_n$, the
membership witness for $n$, and the pointwise rational-history classifier at
the selected unary observation.

Now apply the finite-window restriction handoff of
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff} to any
certified restriction whose visible observation bundle factors through
$S_n$. Since the target bundle is singleton, every visible row is the same
certified $n$-row together with $\mathsf{InBundle}(n,S_n)$ and
$\mathsf{UnaryHistory}(n)$.

Finally read the resulting restricted packet through the pointwise handoff
boundary of \autoref{thm:streamname-regseqrat-pointwise-handoff}. That
boundary has carrier, membership, unary-history, finite-window classifier,
and pointwise rational-history slots only, so it cannot export a regularity
row, a seal classifier, completion data, quotient data, or host-index
equality. The displayed tuple is therefore the whole consumer surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-window restriction handoff]
\label{thm:streamname-regseqrat-finite-window-restriction-handoff}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$\mathcal P:\mathsf{ProbeBundle}$ be a finite observation bundle, and let
$\mathcal Q:\mathsf{ProbeBundle}$ be a certified sub-bundle of $\mathcal P$.
Any pointwise handoff package from $\mathcal P$ restricts to the same
StreamName source rows over $\mathcal Q$: the
$\mathsf{RatStreamNameCarrier}$ rows for $s$ and $t$, the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal Q)$ row,
$\mathsf{UnaryHistory}$, $\mathsf{InBundle}(-,\mathcal Q)$, and the pointwise
$\mathsf{RatHistoryClassifier}$ rows. The restricted packet exports no
$\RegSeqRat$ regularity row, $\RealUp$ seal classifier, completion object,
quotient row, or host-index equality.
\end{theorem}
\begin{proof}
Unfold the finite-window classifier for the smaller certified bundle
$\mathcal Q$. A visible observation over $\mathcal Q$ is a certified unary
history $n$ together with $\mathsf{InBundle}(n,\mathcal Q)$.

Use the sub-bundle evidence to read the same observation as
$\mathsf{InBundle}(n,\mathcal P)$. The pointwise handoff over $\mathcal P$
then supplies exactly the source rows named by
\autoref{thm:streamname-regseqrat-pointwise-handoff}: the carried StreamName
endpoints, unary history evidence, and the pointwise
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ row.

Repack those rows with the membership witness for $\mathcal Q$. This gives
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal Q)$ and the same
pointwise rational-history classifier at each selected observation.

The final packet is still read through the exhaustion boundary of
\autoref{thm:streamname-regseqrat-pointwise-handoff}. Since that boundary
contains only StreamName carrier, finite-window classifier, unary history,
bundle membership, and pointwise classifier rows, the restriction introduces
no regularity, seal, completion, quotient, or host-index-equality datum.
\end{proof}

\begin{theorem}[StreamName RegSeqRat appended-bundle handoff exactness]
\label{thm:streamname-regseqrat-bundle-union-handoff}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, and let
$\mathcal P,\mathcal Q:\mathsf{ProbeBundle}$ be finite observation windows.
Suppose $\mathcal P$ and $\mathcal Q$ each supply the pointwise StreamName
handoff rows for $s$ and $t$: the $\mathsf{RatStreamNameCarrier}$ source
rows, the finite-window classifier row, $\mathsf{UnaryHistory}$ evidence,
membership evidence, and the pointwise $\mathsf{RatHistoryClassifier}$ rows.
Then the appended bundle $\mathsf{BAppend}(\mathcal P,\mathcal Q)$ supplies
exactly the same kind of $\RegSeqRat$ and finite-window $\RealUp$ handoff
rows over the combined window.

Conversely, any consumer read over
$\mathsf{BAppend}(\mathcal P,\mathcal Q)$ restricts to one of the two
component handoff packets. The appended packet exports no $\RegSeqRat$
regularity row, $\RealUp$ seal classifier, completion object, quotient row,
or host-index equality.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_bundle\_union\_handoff}
\begin{proof}
Apply \autoref{thm:streamname-finite-window-union-composition} to the two
finite observation windows. It identifies the visible observations of
$\mathsf{BAppend}(\mathcal P,\mathcal Q)$ with the observations that come
from $\mathcal P$ or from $\mathcal Q$, carrying their original
$\mathsf{InBundle}$ and $\mathsf{UnaryHistory}$ witnesses.

On each component observation, use
\autoref{thm:streamname-regseqrat-pointwise-handoff}. The supplied component
handoff packet gives the carried StreamName endpoints and the pointwise
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ row, and the union composition
repackages those rows into the finite-window classifier for
$\mathsf{BAppend}(\mathcal P,\mathcal Q)$.

For the converse read, restrict the appended window along the selected
component inclusion. Then
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}
recovers exactly the same carrier, classifier, membership, unary-history,
and pointwise rational-history rows over that component packet.

Both directions pass through the pointwise handoff boundary and the
finite-window restriction boundary. Since those boundaries name no
regularity, seal, completion, quotient, or host-index-equality coordinate,
the appended handoff cannot export any such row.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite reindexing coverage]
\label{thm:streamname-regseqrat-pointwise-reindexing-coverage}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$\mathcal P_0,\ldots,\mathcal P_k:\mathsf{ProbeBundle}$ be finite observation
bundles, and let the adjacent stages be connected by certified unary
reindexing maps. Suppose each adjacent reindexing preserves
$\mathsf{UnaryHistory}$, $\mathsf{ProbeBundle}$ membership, $\mathsf{InBundle}$
rows, pointwise $\hsame$ comparisons, and the
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P_i)$ rows carried by
the stage. Then the terminal handoff over $\mathcal P_k$ to $\RegSeqRat$ or to a
finite-window $\RealUp$ consumer is covered by exactly the same pointwise
StreamName rows as the stagewise handoff: the $\mathsf{RatStreamNameCarrier}$
rows for $s$ and $t$, the terminal finite-window classifier, the transported
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}(-,\mathcal P_k)$ evidence, and the
pointwise $\mathsf{RatHistoryClassifier}(s(n),t(n))$ rows at the transported
observations.

The coverage statement is only a finite-window BEDC handoff. It exports no
$\RegSeqRat$ regularity row, no $\RealUp$ seal classifier, no completion object,
no quotient row, and no host-index equality.
\end{theorem}
\begin{proof}
Induct on the finite reindexing schedule. In the empty schedule, the terminal
bundle is the initial bundle, and
\autoref{thm:streamname-regseqrat-pointwise-handoff} gives exactly the listed
StreamName carrier, finite-window classifier, unary-history, membership, and
pointwise rational-history rows.

For the step, assume the coverage packet has been built over $\mathcal P_i$.
The certified unary reindexing map transports the visible unary histories and
their $\mathsf{InBundle}$ witnesses to the next bundle. Apply
\autoref{thm:streamname-regseqrat-observation-stability} to carry the pointwise
$\hsame$ comparisons and the pointwise rational-history classifier rows along
that transported observation.

The next terminal window may discard observations or assemble adjacent visible
pieces. Use \autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}
for the restricted part and
\autoref{thm:streamname-regseqrat-bundle-union-handoff} for the finite bundle
repacking. These two handoff results rebuild the terminal
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P_{i+1})$ row from
the transported pointwise rows.

The induction step therefore preserves the exact public surface named in the
statement. Since every stage passes through the pointwise, restriction, and
bundle-union handoff boundaries, no stage introduces a regularity row, seal
classifier, completion object, quotient row, or host-index equality.
\end{proof}

\begin{theorem}[StreamName RegSeqRat overlap pullback handoff]
\label{thm:streamname-regseqrat-overlap-pullback-handoff}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$\mathcal P,\mathcal Q:\mathsf{ProbeBundle}$ be finite observation bundles,
and let $\mathcal R:\mathsf{ProbeBundle}$ be a certified common sub-bundle
of both $\mathcal P$ and $\mathcal Q$. If the $\mathcal P$-packet and the
$\mathcal Q$-packet each supply the pointwise StreamName-to-$\RegSeqRat$
handoff rows for $s$ and $t$, then their restrictions to $\mathcal R$
classify the same consumer-facing tuple:
$\mathsf{RatStreamNameCarrier}$,
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$,
$\mathsf{UnaryHistory}$, $\mathsf{InBundle}(-,\mathcal R)$, the pointwise
$\hsame$ rows, and $\mathsf{RatHistoryClassifier}$. The common-overlap
packet contains no $\RegSeqRat$ regularity row, $\RealUp$ seal row,
completion row, quotient row, or host-index equality row.
\end{theorem}
\begin{proof}
Restrict the $\mathcal P$-packet to the certified common sub-bundle
$\mathcal R$ by
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}. The
restricted packet exposes the same StreamName carrier rows, the finite-window
classifier over $\mathcal R$, the unary-history and
$\mathsf{InBundle}(-,\mathcal R)$ witnesses, and the pointwise
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ rows.

Apply the same restriction theorem to the $\mathcal Q$-packet. Because both
restricted reads use the same rows $s,t$ and the same certified bundle
$\mathcal R$, the pointwise handoff
\autoref{thm:streamname-regseqrat-pointwise-handoff} identifies both packet
readings with the same consumer-facing tuple on each observation of
$\mathcal R$.

Finally apply
\autoref{thm:streamname-regseqrat-observation-envelope}. The envelope is
closed under the two certified restrictions and contains only carrier,
finite-window, unary-history, membership, pointwise $\hsame$, and
rational-history classifier rows. Hence the pullback over the common overlap
has no coordinate for regularity, seal, completion, quotient, or host-index
equality data.
\end{proof}

\begin{theorem}[StreamName finite observation RealUp seal scope]
\label{thm:streamname-finite-observation-realup-seal-scope}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$\mathcal P:\mathsf{ProbeBundle}$ be finite, and let $n$ be a certified
observation with $\mathsf{UnaryHistory}(n)$ and
$\mathsf{InBundle}(n,\mathcal P)$. A finite-window $\RealUp$ seal consumer of
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$ may read from
StreamName only the carried endpoints for $s$ and $t$, the membership row
$\mathsf{InBundle}(n,\mathcal P)$, the unary observation row
$\mathsf{UnaryHistory}(n)$, and the pointwise classifier row
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

All $\RegSeqRat$ regularity rows, $\RealUp$ seal classifiers, completion
data, quotient data, and host-index equality remain downstream obligations
and are not exported by the finite StreamName observation.
\end{theorem}
\begin{proof}
Begin with the pointwise handoff of
\autoref{thm:streamname-regseqrat-pointwise-handoff}. It exposes the
StreamName endpoint rows, the finite bundle membership row, the unary
observation row, and the pointwise rational-history classifier at the chosen
observation.

For the certified observation $n$, use
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff} to identify the
singleton diagonal view with the same endpoint, membership, unary-history,
and pointwise classifier rows. Then use
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff} to read
the same rows through any certified finite-window restriction of
$\mathcal P$.

Finally apply the obligation separation of
\autoref{thm:streamname-real-regseq-obligation-separation}. It keeps
$\RegSeqRat$ regularity, $\RealUp$ seal classifiers, completion structure,
quotient structure, and host-index equality on the downstream side of the
handoff. The finite observation therefore exports exactly the named
StreamName rows and nothing from the later seal boundary.
\end{proof}

\begin{theorem}[StreamName RegSeqRat observation envelope]
\label{thm:streamname-regseqrat-observation-envelope}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows and let
$\mathcal P$ be a finite $\mathsf{ProbeBundle}$. The observation packet
consisting of $\mathsf{RatStreamNameCarrier}$,
$\mathsf{RatStreamNameFiniteWindowClassifier}$, $\mathsf{UnaryHistory}$,
$\mathsf{InBundle}$, and the pointwise $\hsame$ and
$\mathsf{RatHistoryClassifier}$ rows is closed under certified sub-bundle
restriction and singleton extraction. The packet contains no $\RegSeqRat$
regularity row, no completion row, no quotient row, and no $\RealUp$ seal row.
\end{theorem}
\begin{proof}
For the full finite window, apply
\autoref{thm:streamname-regseqrat-pointwise-handoff}. It identifies the
handoff rows available to $\RegSeqRat$ with the carried StreamName endpoint,
the finite probe bundle, the bundle-membership rows, and the pointwise
rational-history classifier.

For a certified sub-bundle, use
\autoref{thm:streamname-regseqrat-observation-stability}. The same
$\mathsf{RatStreamNameCarrier}$ rows and pointwise $\hsame$ transports are
read after restriction, while membership is replaced by the certified
$\mathsf{InBundle}$ rows of the smaller bundle.

For singleton extraction, apply
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff}. The extracted
observation has exactly one unary history row, its singleton membership
witness, and the corresponding rational-history classifier. Since all three
steps read only these finite observation rows, the envelope has no place for
regularity, completion, quotient, or $\RealUp$ seal data.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-window coverage]
\label{thm:streamname-regseqrat-window-coverage}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows and let
$\mathcal P:\mathsf{ProbeBundle}$ be a finite observation bundle. For every
row of $\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$,
every certified $\mathsf{UnaryHistory}(n)$, and every witness
$\mathsf{InBundle}(n,\mathcal P)$, the exposed observation is exactly the
pointwise row $\mathsf{RatHistoryClassifier}(s(n),t(n))$ together with the
corresponding pointwise $\hsame$ datum. The coverage surface contains no
$\RegSeqRat$ regularity row, completion row, quotient row, or $\RealUp$ seal
row.
\end{theorem}
\begin{proof}
Start with the global handoff of
\autoref{thm:streamname-regseqrat-pointwise-handoff}. It lists the carrier,
finite-window classifier, unary-history, bundle-membership, pointwise
$\hsame$, and rational-history classifier rows as the only rows visible at
the StreamName-to-$\RegSeqRat$ boundary.

The observation stability theorem,
\autoref{thm:streamname-regseqrat-observation-stability}, identifies the
same pointwise $\hsame$ and rational-history row after passing through the
certified bundle observation. The singleton diagonal handoff of
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff} then reads the
selected $n$-row as the diagonal pointwise classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

For an arbitrary finite row, the restriction handoff
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff} reduces
the visible packet to the certified sub-bundle containing that observation.
Finally, the envelope theorem
\autoref{thm:streamname-regseqrat-observation-envelope} removes every
regularity, completion, quotient, and $\RealUp$ seal row from the consumer
surface. Hence the finite-window coverage is exactly the displayed pointwise
classifier row and its membership evidence.
\end{proof}

\begin{theorem}[StreamName RegSeqRat tail reindexing stability]
\label{thm:streamname-regseqrat-tail-reindexing-stability}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, let
$\mathcal P:\mathsf{ProbeBundle}$ be a finite observation bundle, and let
$r:\mathsf{BHist}\to\mathsf{BHist}$ be a certified unary tail schedule whose
selected rows preserve $\mathsf{UnaryHistory}$ and
$\mathsf{InBundle}(-,\mathcal P)$. The StreamName handoff package for $s$
and $t$ transports to the package for $s\circ r$ and $t\circ r$ using only
the reindexed pointwise $\hsame$ rows, the reindexed $\mathsf{UnaryHistory}$
rows, and the transported $\mathsf{InBundle}$ rows. No reindexed packet
imports $\RegSeqRat$ regularity, completion, quotient, host-index equality,
or $\RealUp$ seal data.
\end{theorem}
\begin{proof}
Apply the pointwise handoff
\autoref{thm:streamname-regseqrat-pointwise-handoff} before reindexing. Its
source rows are the StreamName carriers, the finite-window classifier, unary
histories, bundle membership, pointwise $\hsame$, and pointwise
rational-history classifiers.

The certified tail schedule supplies the same observation witnesses after
composition with $r$. By observation stability,
\autoref{thm:streamname-regseqrat-observation-stability}, the transported
rows remain pointwise rows; no global regularity or quotient datum is used.

For each selected row, use the singleton diagonal handoff
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff} to identify
the transported observation with
$\mathsf{RatHistoryClassifier}(s(r(n)),t(r(n)))$. The finite-window
restriction handoff,
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}, repacks
these rows over the reindexed certified sub-bundle.

The observation envelope
\autoref{thm:streamname-regseqrat-observation-envelope} is stable under this
repacking because it names only carrier, finite-window, membership,
unary-history, pointwise $\hsame$, and pointwise rational classifier rows.
Thus the tail-reindexed package is exhausted by the same pointwise handoff
surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-window union seal determinacy]
\label{thm:streamname-regseqrat-finite-window-union-seal-determinacy}
Let $\mathcal P$ and $\mathcal Q$ be certified finite $\mathsf{ProbeBundle}$
observation bundles for StreamName rows $s,t:\mathsf{BHist}\to\mathsf{BHist}$,
and let $\mathcal R$ be their certified finite overlap. Assume that the
$\mathsf{RatStreamNameClassifier}$ rows on $\mathcal R$ match and that the
induced $\RegSeqRat$ handoff packages read the same dyadic finite ledger on
the overlap. Then the union handoff over $\mathcal P\cup\mathcal Q$ determines
a unique $\RegSeqRat$ finite-window seal surface, and the restrictions back to
$\mathcal P$ and to $\mathcal Q$ recover the original displayed seal surfaces.

No regularity row outside the displayed $\RegSeqRat$ handoff, no completion
row, no quotient row, no host-index equality row, and no $\RealUp$ seal row is
introduced by the union.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff} to
$\mathcal P$ and to $\mathcal Q$. Each restriction displays only the StreamName
carrier rows, the finite-window classifier rows, the unary-history and bundle
membership witnesses, and the pointwise rational-history classifier rows.

Use \autoref{thm:streamname-regseqrat-bundle-union-handoff} to assemble these
two displayed packets over $\mathcal P\cup\mathcal Q$. The matching classifier
rows on $\mathcal R$ and the common dyadic finite ledger identify the overlap
as a single source rather than two competing seal readings.

The overlap rows are then compared by
\autoref{thm:streamname-regseqrat-tail-reindexing-stability}. Tail reindexing
preserves the pointwise $\hsame$ rows, the transported unary histories, and
the transported membership witnesses, so the union packet has one displayed
finite-window seal surface on the common part.

Restrict the union packet back to $\mathcal P$ and to $\mathcal Q$ using the
restriction handoff theorem again. Since the union packet contains no row
outside the observation envelope, the two restrictions return exactly the
original displayed handoff surfaces, and the finite-window seal determined by
the union is unique.
\end{proof}

\begin{theorem}[StreamName RegSeqRat pointwise classifier handoff exactness]
\label{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}
For StreamName rows $s,t:\mathsf{BHist}\to\mathsf{BHist}$ and a finite
bundle $\mathcal P:\mathsf{ProbeBundle}$, the consumer-facing handoff from
StreamName observations to $\RegSeqRat$ is exhausted by the
$\mathsf{RatStreamNameCarrier}$ rows, the
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$ rows, bundle
membership, unary observations, pointwise $\hsame$ rows, and pointwise
$\mathsf{RatHistoryClassifier}$ rows. Any datum outside this list is not part
of the handoff interface.
\end{theorem}
\begin{proof}
The base handoff theorem
\autoref{thm:streamname-regseqrat-pointwise-handoff} gives the complete
source packet for the consumer boundary. Its rows already name the carriers,
finite-window classifier, membership witnesses, unary observations,
pointwise $\hsame$, and pointwise rational-history classifiers.

Observation stability,
\autoref{thm:streamname-regseqrat-observation-stability}, shows that moving
inside the finite bundle preserves only these named pointwise rows. The
singleton diagonal handoff,
\autoref{thm:streamname-regseqrat-singleton-diagonal-handoff}, gives the
same conclusion at a single certified observation.

The finite-window restriction handoff
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff} checks
that every certified sub-bundle exposes no additional row. The observation
envelope theorem,
\autoref{thm:streamname-regseqrat-observation-envelope}, closes the
interface by excluding $\RegSeqRat$ regularity, completion, quotient,
host-index equality, and $\RealUp$ seal data. Therefore the listed rows are
exactly the consumer-facing handoff surface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat pointwise hsame closure]
\label{thm:streamname-regseqrat-pointwise-hsame-closure}
Let $s,t,s',t':\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows and let
$\mathcal P:\mathsf{ProbeBundle}$ be finite. Suppose the handoff for
$(s,t)$ is the exact pointwise package of
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness},
and suppose every certified bundled observation carries
$\hsame(s(n),s'(n))$ and $\hsame(t(n),t'(n))$. Then the handoff for
$(s',t')$ is exhausted by the same StreamName carrier rows, restricted
finite-window classifier rows, $\UnaryHistory$ rows, $\mathsf{InBundle}$ rows,
pointwise $\hsame$ rows, and pointwise $\mathsf{RatHistoryClassifier}$ rows.
It accepts no $\RegSeqRat$ regularity, completion, quotient, host-index
equality, or $\RealUp$ seal row.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.RatStreamNameFiniteWindowClassifier\_pointwise\_hsame\_closure}
\begin{proof}
Start with the source packet from
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}.
That theorem gives exactly the carrier, finite-window classifier, bundle,
unary-history, pointwise $\hsame$, and rational-history classifier rows for
the displayed $(s,t)$ handoff.

Transport each certified bundled observation along the given pointwise
$\hsame$ rows. By
\autoref{thm:streamname-regseqrat-observation-stability}, this transport
preserves the unary observations, bundle membership witnesses, and pointwise
rational-history classifier rows, and it does not create any row outside the
StreamName observation surface.

For a restricted finite window, apply
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}. The
restriction keeps the same finite carrier rows and classifier rows over the
sub-bundle, now read through $(s',t')$.

Finally use \autoref{thm:streamname-regseqrat-observation-envelope}. The
envelope excludes $\RegSeqRat$ regularity, completion, quotient, host-index
equality, and $\RealUp$ seal data from the observation handoff, so the
transported packet is closed under pointwise $\hsame$ exactly on the listed
consumer interface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat pointwise hsame transport composition]
\label{thm:streamname-regseqrat-pointwise-hsame-transport-composition}
Let $s,t,s',t',s'',t'':\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows,
and let $\mathcal P:\mathsf{ProbeBundle}$ be finite. Suppose the handoff for
$(s,t)$ is the exact pointwise package of
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}.
Suppose also that every certified bundled observation $n$ carries
$\hsame(s(n),s'(n))$, $\hsame(t(n),t'(n))$, $\hsame(s'(n),s''(n))$, and
$\hsame(t'(n),t''(n))$. Then the handoff for $(s'',t'')$ is exhausted by the
same $\mathsf{RatStreamNameCarrier}$ rows, restricted finite-window classifier
rows, $\UnaryHistory$ rows, $\mathsf{InBundle}$ rows, pointwise $\hsame$ rows,
and pointwise $\mathsf{RatHistoryClassifier}$ rows. It accepts no $\RegSeqRat$
regularity, completion, quotient, host-index equality, or $\RealUp$ seal row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-pointwise-hsame-closure} to the exact
handoff for $(s,t)$ and the displayed observations from $(s,t)$ to
$(s',t')$. This gives the same carrier, finite-window, unary-history,
bundle-membership, pointwise $\hsame$, and rational-history classifier surface
for the intermediate handoff.

Next compose the observation rows pointwise. For each certified bundled
observation $n$, transitivity of $\hsame$ composes
$\hsame(s(n),s'(n))$ with $\hsame(s'(n),s''(n))$, and composes
$\hsame(t(n),t'(n))$ with $\hsame(t'(n),t''(n))$. Thus the intermediate
handoff has the exact pointwise transport data needed for the second step.

Apply \autoref{thm:streamname-regseqrat-pointwise-hsame-closure} again, now
from $(s',t')$ to $(s'',t'')$. The conclusion is the displayed handoff for
$(s'',t'')$ on the original finite bundle $\mathcal P$ with no new row outside
the consumer-facing observation surface.

The exclusion clause is inherited at both applications of the closure theorem:
neither step reads $\RegSeqRat$ regularity, completion, quotient,
host-index equality, or $\RealUp$ seal data. Therefore the two transported
handoffs compose inside the same finite-window pointwise interface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat pointwise hsame transport confluence]
\label{thm:streamname-regseqrat-pointwise-hsame-transport-confluence}
Let $s,t,u,v:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, and let
$\mathcal P:\mathsf{ProbeBundle}$ be finite. Let
$$
\begin{gathered}
(s_0,t_0),\ldots,(s_m,t_m),\\
(r_0,q_0),\ldots,(r_k,q_k)
\end{gathered}
$$
be two finite pointwise $\hsame$ transport schedules of StreamName row pairs
with common endpoints
$$
(s_0,t_0)=(r_0,q_0)=(s,t),
\qquad
(s_m,t_m)=(r_k,q_k)=(u,v).
$$
Assume the handoff for $(s,t)$ is the exact pointwise package of
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}.
Assume further that every adjacent stage of both schedules carries the
certified bundled pointwise $\hsame$ rows and preserves that exact pointwise
package. Then the two induced handoff packets at $(u,v)$ expose the same
$\mathsf{RatStreamNameCarrier}$ rows, restricted finite-window classifier
rows, $\UnaryHistory$ rows, $\mathsf{InBundle}$ rows, pointwise $\hsame$ rows,
and pointwise $\mathsf{RatHistoryClassifier}$ rows. Neither packet exposes a
$\RegSeqRat$ regularity row, completion row, quotient row, host-index equality
row, or $\RealUp$ seal row.
\end{theorem}
\begin{proof}
Induct over the first finite schedule. The base case is the source handoff
itself, whose exact consumer-facing package is supplied by
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}.
For the step case, apply
\autoref{thm:streamname-regseqrat-pointwise-hsame-transport-composition} to
compose the accumulated transport with the next adjacent pointwise $\hsame$
stage.

The same induction applies to the second finite schedule. Its base is the
same exact package at $(s,t)$, and each step preserves the displayed carrier,
finite-window, unary-history, bundle-membership, pointwise $\hsame$, and
rational-history classifier rows by the same composition theorem.

Both inductions therefore terminate at the common endpoint $(u,v)$ with the
pointwise package of
\autoref{thm:streamname-regseqrat-pointwise-classifier-handoff-exactness}.
Comparing through that endpoint package identifies the exposed carrier,
restricted finite-window classifier, $\UnaryHistory$, $\mathsf{InBundle}$,
pointwise $\hsame$, and pointwise $\mathsf{RatHistoryClassifier}$ rows from
the two routes.

Finally apply \autoref{thm:streamname-regseqrat-observation-envelope} at the
common endpoint. The envelope excludes $\RegSeqRat$ regularity, completion,
quotient, host-index equality, and $\RealUp$ seal rows from the observation
handoff, so neither route can expose any row outside the common pointwise
StreamName interface.
\end{proof}

\begin{theorem}[StreamName RegSeqRat restricted pointwise transport confluence]
\label{thm:streamname-regseqrat-pointwise-restricted-transport-confluence}
Let $s,t,u,v:\mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, and let
$\mathcal Q\subseteq\mathcal P$ be a certified finite subbundle. Suppose two
finite pointwise $\hsame$ transport schedules for $(s,t)$ have common endpoint
$(u,v)$ as in
\autoref{thm:streamname-regseqrat-pointwise-hsame-transport-confluence}. After
restricting each transported handoff to $\mathcal Q$, the two restricted packets
expose the same $\mathsf{RatStreamNameCarrier}$ rows, restricted finite-window
classifier rows, $\UnaryHistory$ rows, $\mathsf{InBundle}$ rows, pointwise
$\hsame$ rows, and pointwise $\mathsf{RatHistoryClassifier}$ rows to every
$\RegSeqRat$ handoff and every finite-window $\RealUp$ consumer. The restricted
packets expose no $\RegSeqRat$ regularity row, completion row, quotient row,
host-index equality row, or $\RealUp$ seal row.
\end{theorem}
\begin{proof}
Begin with the two endpoint handoffs supplied by
\autoref{thm:streamname-regseqrat-pointwise-hsame-transport-confluence}. That
confluence theorem identifies the carrier, finite-window classifier,
$\UnaryHistory$, $\mathsf{InBundle}$, pointwise $\hsame$, and
$\mathsf{RatHistoryClassifier}$ rows at the common endpoint $(u,v)$.

Restrict both endpoint packets along the certified inclusion
$\mathcal Q\subseteq\mathcal P$. By
\autoref{thm:streamname-regseqrat-finite-window-restriction-handoff}, restriction
forgets only observations outside $\mathcal Q$ and preserves every displayed row
of the finite-window handoff on the subbundle.

It remains to check the consumer boundary. Apply
\autoref{thm:streamname-regseqrat-observation-envelope} after restriction. The
envelope is already stated only in terms of the exposed StreamName observation
rows, so it is stable under passing from $\mathcal P$ to $\mathcal Q$.

Thus every $\RegSeqRat$ handoff and every finite-window $\RealUp$ consumer sees
the same restricted carrier, classifier, history, membership, pointwise
$\hsame$, and rational-history rows through either route. The same envelope
excludes regularity, completion, quotient, host-index equality, and $\RealUp$
seal data from the restricted packets.
\end{proof}
