\section{StreamName RegSeqRat Real public seal boundary}
\label{sec:streamname-regseqrat-real-public-seal-boundary}

\begin{theorem}[StreamName-RegSeqRat-Real public seal no-quotient boundary]
\label{thm:streamname-regseqrat-real-public-seal-no-quotient}
Every public $\RealUp$ seal route exported from the $\StreamNameUp$
finite-window handoff and consumed by $\RegSeqRatUp$ factors through the finite
$\BHist$ rows, pointwise $\hsame$ rows, $\Cont$ routes, $\Pkg$ provenance, and
local $\NameCert$ rows already exposed by
\autoref{thm:streamname-real-regseq-finite-window-handoff},
\autoref{thm:streamname-regseqrat-real-seal-composition}, and
\autoref{thm:streamname-realup-seal-boundary}. The handoff exports no quotient
stream equality, selected limit, host real equality, ambient completeness
claim, or open-cover compactness claim.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-real-regseq-finite-window-handoff}. It
identifies the public StreamName source surface as a finite-window packet: the
selected history rows, the finite $\mathsf{ProbeBundle}$ ledger, membership
rows, unary-history rows, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ support.

Next apply \autoref{thm:streamname-regseqrat-real-seal-composition}. The
RegSeqRat consumer reads the same finite packet through the regular-sequence
seal route, so the Real-facing seal is reached through the displayed finite
rows and their provenance rather than through a hidden stream equality or a
chosen completed value.

Finally apply \autoref{thm:streamname-realup-seal-boundary}. That boundary
keeps the RealUp seal at the finite-window interface and excludes quotient
streams, selected limits, host real equality, and ambient completeness data.
The sibling L10 consumers
\autoref{ch:concrete-instances-regseqrat-namecert},
\autoref{ch:concrete-instances-dyadicratcore-namecert}, and
\autoref{ch:concrete-instances-real-namecert} therefore receive only the
displayed finite rows and local certificates, not an open-cover compactness
claim.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-Real public seal finite-section determinacy]
\label{thm:streamname-regseqrat-real-public-seal-finite-section-determinacy}
Let $\mathcal S_0$ and $\mathcal S_1$ be public $\RealUp$ seal routes exported
from the $\StreamNameUp$ finite-window handoff and consumed by
$\RegSeqRatUp$. Suppose they display the same $\StreamNameUp$ finite section,
the same $\DyadicRatCoreUp$ ledger rows, the same $\RegSeqRatUp$ regularity
and classifier rows, the same local $\RealUp$ finite-section readback, and the
same support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then $\mathcal S_0$ and $\mathcal S_1$ determine the same finite public seal
section.

This determinacy is only a statement about the public finite section of the
BEDC ledger. It does not assert quotient-stream equality, selected limits,
host real equality, countable choice, ambient completeness, an aggregate
formalstatus row, bridge rows, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-finite-section-pullback-exactness} and
\autoref{thm:streamname-finite-section-real-regseq-dyadic-lock}. The common
StreamName finite section is pulled back to the same DyadicRatCore ledger,
RegSeqRat readback, local Real seal row, and displayed support rows.

Next apply \autoref{thm:regseqrat-terminal-four-face-source-uniqueness}. Since
the two routes expose the same StreamName window, dyadic ledger, RegSeqRat
regularity and classifier rows, local Real readback, and support rows, they
come from one common finite RegSeqRat source section.

Now apply \autoref{thm:real-terminal-finite-section-pullback-exactness}. The
local Real readback of each route is accepted exactly through the same ordered
four-face packet over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$.

The two public seal routes are therefore projections of one finite BEDC
ledger. Projecting that ledger to the public seal coordinate gives the same
finite public seal section for $\mathcal S_0$ and $\mathcal S_1$, and the
excluded quotient, limit, host-equality, choice, completeness, aggregate
status, and bridge coordinates have no displayed row from which to vary.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-Real public seal window induction]
\label{thm:streamname-regseqrat-real-public-seal-window-induction}
Every public $\RealUp$ seal section exported from a $\StreamNameUp$
finite-window handoff and consumed by $\RegSeqRatUp$ is generated by induction
over the displayed finite rows. The generating rows are precisely the visible
$\StreamNameUp$ window row, the $\DyadicRatCoreUp$ ledger rows, the
$\RegSeqRatUp$ regularity and classifier rows, the local $\RealUp$ readback
row, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
The induction step appends one visible window row and preserves the same
public seal section exactly when the finite-section determinacy hypotheses of
\autoref{thm:streamname-regseqrat-real-public-seal-finite-section-determinacy}
are preserved.

The generated section contains no quotient stream equality, selected limit,
host real equality, countable choice, metric-completeness datum, bridge row, or
ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
The base section is the empty displayed window together with its finite support
rows. Apply
\autoref{thm:streamname-regseqrat-real-public-seal-no-quotient}. It identifies
the public seal boundary as a route through the finite $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows and supplies no quotient, limit,
host-equality, choice, completeness, or bridge coordinate.

For the induction step, append one visible $\StreamNameUp$ window row and its
matching dyadic, RegSeqRat, local Real, and support rows. Apply
\autoref{thm:streamname-finite-section-pullback-exactness} and
\autoref{thm:streamname-finite-section-real-regseq-dyadic-lock} to transport
the appended window through the same finite four-face packet.

Next apply \autoref{thm:regseqrat-terminal-four-face-source-uniqueness}. The
RegSeqRat consumer sees only the displayed window, ledger, regularity,
classifier, readback, and support rows, so the source section after the append
is the unique finite source section with those rows.

Finally apply
\autoref{thm:real-terminal-finite-section-pullback-exactness} and then
\autoref{thm:streamname-regseqrat-real-public-seal-finite-section-determinacy}.
The local Real readback is accepted through the same ordered four-face packet,
and determinacy says that preserving the displayed finite rows preserves the
same public seal section. Since every step appends only such rows, the whole
public section is generated by the stated finite-window induction.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-Real public seal support intersection]
\label{thm:streamname-regseqrat-real-public-seal-support-intersection}
Let $\mathcal S_0$ and $\mathcal S_1$ be public $\RealUp$ seal routes exported
from the $\StreamNameUp$ finite-window handoff and consumed by $\RegSeqRatUp$.
Suppose their visible rows agree on the $\StreamNameUp$ finite section, the
$\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ regularity and classifier rows,
the local $\RealUp$ readback, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then $\mathcal S_0$ and $\mathcal S_1$ have the same finite support
intersection inside the public seal table. Any disagreement in that
intersection either deletes one of the displayed rows or introduces a
coordinate outside the public table exposed by the seal route.

The assertion is only about the common finite support of the two displayed
routes. It does not identify quotient streams, select limits, assert host real
equality, add bridge rows, or invoke ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-real-public-seal-no-quotient}. It identifies
the public seal inventory as exactly the displayed finite-window rows, dyadic
ledger rows, RegSeqRat regularity and classifier rows, local Real readback, and
the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next apply
\autoref{thm:streamname-regseqrat-real-public-seal-finite-section-determinacy}.
The hypotheses say that the two routes agree on every row that can appear in
the public seal section, so projecting either route to the visible support table
gives the same finite section.

Finally apply
\autoref{thm:streamname-regseqrat-real-public-seal-window-induction}. Appending
visible rows preserves the section precisely when the displayed window, ledger,
classifier, readback, and support rows are preserved. Thus a proposed
difference in the support intersection has only two possibilities: it removes a
displayed row already fixed by the common section, or it names a coordinate that
the no-quotient boundary says is not in the public seal table.
\end{proof}
