\section{StreamName RegularCauchyName Lattice Link}
\label{sec:streamname-regularcauchyname-lattice-link}

\begin{theorem}[StreamName scheduled-window RegularCauchyName link]
\label{thm:streamname-regularcauchyname-lattice-link}
Every $\StreamNameUp$ finite-window schedule consumed by $\RegularCauchyNameUp$ is read as the scheduled-window sibling route of \autoref{ch:concrete-instances-regular-cauchy-name-namecert}. The route carries the displayed window rows, certified unary observations, pointwise $\RegSeqRatUp$ classifier rows, transport data, continuation data, package provenance, and local naming rows into the regular Cauchy name packet. It exports no host sequence, quotient-stream equality, selected limit, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with the finite-window rows already displayed in the $\StreamNameUp$ packet. The public interface and lattice dependency rows expose scheduled windows, bundle membership, certified unary observations, pointwise $\RegSeqRatUp$ classifier data, componentwise $\hsame$ transport, displayed $\Cont$ routes, package provenance, and local naming.

The $\RegularCauchyNameUp$ handoff of \autoref{ch:concrete-instances-regular-cauchy-name-namecert} consumes exactly that scheduled-window surface before exposing its dyadic-radius row, regularity ledger, and $\RealUp$ seal. Hence the StreamName schedule is not a free-floating kernel row; it is the window sibling route through which the regular Cauchy name reads its source observations.

The non-escape clause is coordinate exhaustion. Neither the StreamName finite-window package nor the RegularCauchyName handoff contains a host sequence, quotient-stream equality, selected limit, independent real carrier, or ambient completeness coordinate, so the routed lattice link cannot export one.
\end{proof}

\begin{theorem}[StreamName real-seal lattice route]
\label{thm:streamname-real-seal-lattice-link}
Every accepted $\StreamNameUp$ finite-window schedule consumed by $\RegularCauchyNameUp$ reaches the $\RealUp$ seal only through the displayed route
$$
\StreamNameUp\ \text{window rows}
\longrightarrow
\RegularCauchyNameUp\ \text{schedule, radius, ledger, and seal rows}
\longrightarrow
\RegSeqRatUp\ \text{regular source rows}
\longrightarrow
\RealUp\ \text{seal row}.
$$
The $\RegularCauchyNameUp$ segment is the schedule-and-radius packet of \autoref{ch:concrete-instances-regular-cauchy-name-namecert}, the $\RegSeqRatUp$ segment is the regular source handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal is the real-facing packet of \autoref{ch:concrete-instances-real-namecert}. The route exports no quotient stream equality, selected limit, host sequence equality, host real equality, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the StreamName-to-RegularCauchyName lattice edge of \autoref{thm:streamname-regularcauchyname-lattice-link}. It identifies the accepted finite-window schedule as the only surface through which $\RegularCauchyNameUp$ reads the source observations, together with the displayed certified unary observations, pointwise $\RegSeqRatUp$ classifier rows, transport rows, continuation rows, package provenance, and local naming data.

The $\RegularCauchyNameUp$ packet then exposes the dyadic-radius row, regularity ledger, and real-seal-facing row named in \autoref{ch:concrete-instances-regular-cauchy-name-namecert}. The regular source information is the same finite-window $\RegSeqRatUp$ handoff recorded in \autoref{ch:concrete-instances-regseqrat-namecert}, so the route cannot bypass the regular rational source rows before reaching the real-facing seal.

Finally, the terminal consumer is the $\RealUp$ seal row of \autoref{ch:concrete-instances-real-namecert}. Coordinate exhaustion now gives the non-escape clause: none of the displayed packets contains a quotient stream equality, selected limit, host sequence equality, host real equality, or ambient completeness coordinate, and therefore no such coordinate is exported by their composite route.
\end{proof}

\begin{theorem}[StreamName pointwise reindexing RegularCauchyName route]
\label{thm:streamname-regularcauchyname-pointwise-reindexing-route}
Let a public $\StreamNameUp$ finite-window schedule be reindexed pointwise by unary observation rows and transported componentwise by displayed $\hsame$ rows, as in \autoref{thm:rat-stream-name-carrier-pointwise-hsame-transport} and \autoref{thm:rat-stream-name-transported-successor-reindexing-stability}. Then every accepted $\RegularCauchyNameUp$ consumer reads the reindexed schedule only through the scheduled-window route of \autoref{thm:streamname-regularcauchyname-lattice-link}, and the route to the $\RealUp$ seal is exactly the route of \autoref{thm:streamname-real-seal-lattice-link}. The displayed rows are precisely the $\mathsf{BHist}$ observation rows, $\mathsf{UnaryHistory}$ certificates, componentwise $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, local $\NameCert$ rows, pointwise $\RegSeqRatUp$ classifier rows, and the terminal $\RealUp$ seal row. The consumer exports no quotient stream equality, host sequence equality, selected limit, host real equality, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with the public finite-window $\StreamNameUp$ schedule and its unary reindexing row. The pointwise carrier transport theorem \autoref{thm:rat-stream-name-carrier-pointwise-hsame-transport} carries each certified unary observation along its displayed $\hsame$ row, while \autoref{thm:rat-stream-name-transported-successor-reindexing-stability} repacks the transported observations as the finite-window classifier surface read by the reindexed schedule.

Now apply \autoref{thm:streamname-regularcauchyname-lattice-link}. It forces every accepted $\RegularCauchyNameUp$ consumer to read the transported schedule through the same scheduled-window sibling route, so the only available data are the $\mathsf{BHist}$ rows, $\mathsf{UnaryHistory}$ certificates, pointwise $\RegSeqRatUp$ classifier rows, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows.

Finally compose with \autoref{thm:streamname-real-seal-lattice-link}. The seal read reaches $\RealUp$ only after the transported StreamName window has passed through the RegularCauchyName schedule, radius, ledger, and seal rows. Coordinate exhaustion gives the non-escape clause: none of these displayed rows contains quotient stream equality, host sequence equality, a selected limit, host real equality, or ambient completeness data, so the reindexing route cannot export any such coordinate.
\end{proof}
