\begin{theorem}[StreamName RegSeqRat RealUp seal source determinacy]
\label{thm:streamname-regseqrat-realup-seal-source-determinacy}
Let $W$ be a finite public $\StreamNameUp$ rational observation window, and
let $\mathcal{E}_0$ and $\mathcal{E}_1$ be finite-window $\RealUp$ seal
packages induced from $W$. Suppose both packages read the same accepted
$\RegSeqRat$ spine over $W$, the same DyadicRatCore endpoint ledger, the same
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, the same unary
observation rows, the same finite $\Cont$ ledger, the same displayed $\hsame$
endpoint transports, and the same $\Pkg$ provenance. Then $\mathcal{E}_0$ and
$\mathcal{E}_1$ have the same visible seal source.

That source is exactly the public StreamName finite-window row, the accepted
$\RegSeqRat$ finite-window seal row, the dyadic endpoint rows, and the shared
ledger boundary. It contains no completion row, quotient row, host index
equality, or off-ledger $\RealUp$ classifier.
\end{theorem}
\begin{proof}
First exhaust the scheduled seal package. Apply
\autoref{thm:streamname-regseqrat-scheduled-seal-exhaustion}. Both induced
packages project to the same scheduled StreamName row, accepted $\RegSeqRat$
finite-window seal row, and finite-window $\RealUp$ ledger boundary, because
the listed public window, spine, dyadic endpoint, bundle, transport, and
provenance rows agree.

Next compare the pointwise seal rows. Use
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} at each certified
unary observation of $W$. The shared DyadicRatCore endpoint ledger fixes the
pointwise seal classifier rows under the displayed $\hsame$ transports, so the
two packages cannot choose different visible rational endpoints.

Now pass from pointwise rows to the whole finite window. By
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal}, the public
StreamName window, the scheduled $\RegSeqRat$ seal, and every nested handoff
select one finite observation packet with the same $\mathsf{ProbeBundle}$,
$\Cont$, $\hsame$, and $\Pkg$ rows.

Finally apply \autoref{thm:streamname-realup-seal-boundary}. Every
finite-window $\RealUp$ seal read arising from this handoff factors through
the same StreamName row, accepted $\RegSeqRat$ seal row, dyadic endpoint rows,
and shared ledger boundary. Since none of the cited boundary theorems exports
completion rows, quotient rows, host index equality, or off-ledger classifiers,
the visible seal source of $\mathcal{E}_0$ and $\mathcal{E}_1$ is determined
by the stated handoff data.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp seal source minimality]
\label{thm:streamname-regseqrat-realup-seal-source-minimality}
Let $W$ be a finite public $\StreamNameUp$ rational observation window, and
let $\mathcal{E}$ be a finite-window $\RealUp$ seal package induced from $W$
and an accepted $\RegSeqRat$ spine. Then every visible source row used by
$\mathcal{E}$ is one of the public StreamName finite-window row, the accepted
$\RegSeqRat$ finite-window seal row, the dyadic endpoint ledger, the
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, the unary history rows,
the finite $\Cont$ ledger, the displayed $\hsame$ endpoint transports, or the
$\Pkg$ provenance.

In particular, no completion carrier, quotient representative, host-index
equality, or off-ledger $\RealUp$ classifier is a source row of the induced
finite-window seal package.
\end{theorem}
\begin{proof}
Start with
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy} applied to
two reads of the same induced package. The determinacy statement identifies
the visible source with the public StreamName finite-window row, the accepted
$\RegSeqRat$ finite-window seal row, the dyadic endpoint rows, and the shared
ledger boundary.

Use \autoref{thm:streamname-regseqrat-scheduled-seal-exhaustion} to expand the
scheduled seal boundary. The expansion lists only the accepted spine rows,
bundle rows, unary observation rows, continuation rows, endpoint transports,
and provenance named in the statement.

Finally apply \autoref{thm:streamname-realup-seal-boundary}. Its boundary
factorization is through exactly those finite-window rows, so any alleged
source outside the listed tuple would have to enter through a completion,
quotient, host-index, or off-ledger classifier row. The boundary theorem
exports none of those rows, establishing the stated minimality.
\end{proof}

\begin{theorem}[StreamName RegSeqRat RealUp seal unique source]
\label{thm:streamname-regseqrat-realup-seal-source-unique-source}
Let $\mathcal{E}_0$ and $\mathcal{E}_1$ be finite-window $\RealUp$ seal
packages induced from public StreamName windows and accepted $\RegSeqRat$
spines. Suppose they agree on exactly the minimal source tuple consisting of
the public StreamName finite-window row, accepted $\RegSeqRat$ finite-window
seal row, dyadic endpoint ledger, $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ rows, unary history rows, finite $\Cont$ ledger, displayed
$\hsame$ endpoint transports, and $\Pkg$ provenance. Then every downstream
$\RegSeqRat$ or $\RealUp$ finite-window consumer sees the same visible seal
source from $\mathcal{E}_0$ and $\mathcal{E}_1$.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-realup-seal-source-minimality} to both
packages. Each visible source is confined to the same finite tuple of public
window, accepted seal, endpoint, bundle, history, continuation, transport, and
provenance rows.

The assumed agreement on that tuple supplies the hypotheses of
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy}. Hence the
two packages have the same visible seal source.

Any downstream finite-window $\RegSeqRat$ or $\RealUp$ consumer reads through
that visible source tuple and not through completion, quotient, host-index, or
off-ledger classifier data. Therefore the consumer observations obtained from
$\mathcal{E}_0$ and $\mathcal{E}_1$ coincide on the visible seal source.
\end{proof}
