\section{StreamName Real-RegSeq shared-tail budget route}
\label{sec:streamname-real-regseq-shared-tail-budget-route}

\begin{theorem}[StreamName Real-RegSeq shared-tail budget route]
\label{thm:streamname-real-regseq-shared-tail-budget-route}
Let $W_0$ and $W_1$ be accepted finite $\StreamNameUp$ windows consumed by a
$\RegSeqRatUp$ readback route, by a finite-window $\RealUp$ seal route, or by a
shared-tail route that serves both consumers. Suppose the two reads pass
through the same $\DyadicTailRadiusLedgerUp$ coverage row of
\autoref{thm:dyadic-tail-radius-ledger-tail-budget-coverage} and the same
$\RegularCauchyTailMeetUp$ shared-threshold row of
\autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate}.
Then every public seal or readback consumer of the two windows factors through
exactly the finite StreamName window rows, $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, the dyadic tail-radius ledger,
the shared threshold, the $\RegSeqRatUp$ readback, and the $\RealUp$
finite-window ledger boundary.

The route exports no quotient stream, host real equality, selected limit,
independent tail oracle, countable-choice selector, or completeness principle.
\end{theorem}
\begin{proof}
Start with the local finite-window budget handoff. By
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff}, every
regularity row, dyadic tolerance row, and $\RealUp$ seal row consumed from a
finite $\StreamNameUp$ window is downstream of $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, $\mathsf{UnaryHistory}$, the observation-budget surface,
and the tail-budget rows.

Use the sibling StreamName route
\autoref{thm:streamname-budget-handoff-sibling-chapter-route} to keep this
handoff inside the same finite observation-budget and tail-budget chain. The
accepted windows $W_0$ and $W_1$ therefore present public data only through
their displayed finite window rows and their attached transport, continuation,
package, and naming rows.

Now read the common dyadic ledger. Apply
\autoref{thm:dyadic-tail-radius-ledger-tail-budget-coverage} to place each
admitted tail-radius read inside the finite precision, tail-window,
StreamName-window, and dyadic readback rows. Then apply
\autoref{thm:dyadic-tail-radius-ledger-regseq-real-handoff} to route the
$\RegSeqRatUp$ readback and the $\RealUp$ seal boundary after that same ledger
row.

Finally attach the shared threshold. The public shared-threshold certificate
\autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate}
exposes the paired source, window, modulus, dyadic threshold, comparison,
transport, continuation, provenance, and local naming rows, while
\autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}
fixes the displayed threshold ledger for duplicate transported reads of the
same source-window-modulus route.

The carrier inventory is now exhausted. A consumer can project only the finite
StreamName windows, $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$,
$\mathsf{UnaryHistory}$, the dyadic tail-radius ledger, the shared threshold,
the $\RegSeqRatUp$ readback, and the $\RealUp$ finite-window ledger boundary,
together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows. None of the cited carriers contains a quotient stream, host
real equality witness, selected limit, independent tail oracle,
countable-choice selector, or completeness principle, so none can escape
through the public route.
\end{proof}

\begin{theorem}[StreamName shared-tail window pullback exactness]
\label{thm:streamname-shared-tail-window-pullback-exactness}
Let $W_0$ and $W_1$ be accepted finite $\StreamNameUp$ windows, and let
$$
S=(M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N)
$$
be an accepted $\CauchySharedTailModulusUp$ packet whose displayed windows are
the same $W_0$ and $W_1$. Every $\RealUp$ seal read or $\RegSeqRatUp$ readback
pullback from these windows factors through the shared threshold $\tau$, the
dyadic ledger $D$, the paired windows $W_0,W_1$, the paired readbacks
$Q_0,Q_1$, and the seal route $E,H,C,P,N$ displayed by $S$.

Replacing one side by a private threshold, quotient stream, selected limit,
host real equality, or independent inverse-budget route is not a read of the
packet $S$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-real-regseq-shared-tail-budget-route}. It places
the two finite windows on the common StreamName budget path through the dyadic
tail-radius ledger, the shared threshold, the $\RegSeqRatUp$ readback boundary,
and the $\RealUp$ finite-window seal boundary.

Now read the $\CauchySharedTailModulusUp$ packet through
\autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}. It identifies any
seal-facing consumer with the rows
$M_0,M_1,\tau,D,W_0,W_1,Q_0,Q_1,E,H,C,P,N$. The paired-window service of
\autoref{thm:cauchy-shared-tail-modulus-paired-window-readback-service} keeps
the two windows attached to the same threshold and dyadic ledger.

Finally compare reciprocal-window consumers only through the
\autoref{thm:cauchy-inverse-budget-streamname-window-dependency}. That
comparison supplies no private threshold, quotient stream, selected limit, host
real equality, or independent inverse-budget route, so every displayed pullback
remains the read of the single packet $S$.
\end{proof}
