\section{StreamName Synchronized Window Union}
\label{sec:streamname-synchronized-window-union}

\begin{theorem}[StreamName synchronized-window carrier union]
\label{thm:streamname-synchronized-window-union-carrier}
Let $\mathcal W_L$ and $\mathcal W_R$ be displayed finite
$\StreamNameUp$ windows over certified source maps $s,t$, and let
$\mathcal R$ be a certified common-refinement package whose generated
$\mathsf{ProbeBundle}$ restricts to the selected bundles of both windows. If
the selected rows of $\mathcal W_L$ and $\mathcal W_R$ agree through the
displayed common-refinement $\hsame$ and $\Cont$ ledger, then the two windows
repack into one synchronized $\StreamNameUp$ carrier row over $\mathcal R$.

The synchronized row contains exactly the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal R)$ row, the
displayed $\mathsf{ProbeBundle}$ row, the $\mathsf{InBundle}$ membership
rows, the certified $\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, and the shared $\hsame/\Cont/\Pkg$
provenance rows.
\end{theorem}
\begin{proof}
Project both windows through
\autoref{thm:streamname-common-refinement-source-determinacy}. The common
refinement determines the same StreamName source tuple on the left and on the
right, so the selected classifier, bundle membership, unary-history, pointwise
rational-history, $\hsame$, $\Cont$, and $\Pkg$ rows are already one displayed
tuple over $\mathcal R$.

Use \autoref{thm:streamname-tail-window-cover-common-refinement} to read the
generated common window as a finite tail-window packet. Its restriction
clauses are precisely the restrictions back to $\mathcal W_L$ and
$\mathcal W_R$.

Repack the projected rows as the synchronized StreamName carrier row. The
carrier has no coordinate for a quotient stream, host function, completion
object, or external index equality, so the repacking uses only the displayed
finite-window rows.
\end{proof}

\begin{theorem}[StreamName synchronized-window RegSeqRat seal handoff]
\label{thm:streamname-synchronized-window-regseqrat-seal}
Let $\mathcal S$ be the synchronized $\StreamNameUp$ carrier row obtained from
\autoref{thm:streamname-synchronized-window-union-carrier}. Then every
$\RegSeqRat$ handoff read from $\mathcal S$ preserves the endpoint, radius,
regularity, readback, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows consumed
by the finite $\RealUp$ seal.

Equivalently, the downstream consumer reads one synchronized boundary: the
StreamName finite-window source rows of $\mathcal S$, the accepted
$\RegSeqRat$ endpoint and regularity rows selected from those sources, and the
finite $\RealUp$ seal ledger rows. No route through the original left or right
window contributes an additional consumer-visible row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-synchronized-window-union-carrier}. This
places both displayed windows over one carrier row whose finite-window source
tuple is independent of the left or right route.

Next apply \autoref{thm:streamname-regseqrat-common-window-transport}. The
synchronized carrier is a common-window surface, so the $\RegSeqRat$ handoff
rows transported through the two original windows are the same
consumer-facing rows.

Apply \autoref{thm:streamname-regseqrat-dyadic-source-determinacy} to identify
the DyadicRatCore endpoint and radius rows read from the accepted
$\RegSeqRat$ spine. Then use
\autoref{thm:streamname-regseqrat-realup-source-boundary-exhaustion} to list
the rows consumed by the terminal finite $\RealUp$ seal.

The listed families include endpoint, radius, regularity, readback,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. Since each family is
projected from the synchronized row or from the accepted $\RegSeqRat$ spine,
there is no remaining route-dependent row to expose.
\end{proof}

\begin{theorem}[StreamName synchronized-window NameCert boundary]
\label{thm:streamname-synchronized-window-namecert-boundary}
The synchronized-window rows of
\autoref{thm:streamname-synchronized-window-union-carrier} and
\autoref{thm:streamname-synchronized-window-regseqrat-seal} form the local
$\NameCert_{\StreamNameUp}$ obligation boundary needed by the
$\RegSeqRat/\RealUp$ seal consumer. The boundary consists of finite carrier
rows, common-refinement source determinacy, synchronized common-window
transport, accepted $\RegSeqRat$ endpoint and regularity rows, and the finite
seal ledger consumed by $\RealUp$.

This boundary contains no quotient stream, host function, external real,
completion theorem, or real-completeness principle.
\end{theorem}
\begin{proof}
Read the carrier face from
\autoref{thm:streamname-synchronized-window-union-carrier}. It supplies the
finite synchronized StreamName row and identifies its left and right
restrictions through common-refinement source determinacy.

Read the consumer face from
\autoref{thm:streamname-synchronized-window-regseqrat-seal}. It preserves the
$\RegSeqRat$ endpoint, radius, regularity, readback, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows passed to the finite $\RealUp$ seal.

Together these two faces exhaust the local obligation boundary: the producer
side supplies finite synchronized StreamName rows, and the consumer side reads
only the displayed $\RegSeqRat/\RealUp$ seal rows. The excluded quotient,
host-function, external-real, completion, and real-completeness objects have
no coordinate in either face.
\end{proof}

\begin{theorem}[StreamName synchronized-window classifier coverage]
\label{thm:streamname-synchronized-window-union-classifier-coverage}
Let $\mathcal W_L$ and $\mathcal W_R$ be displayed finite
$\StreamNameUp$ windows over certified maps $s,t$, and let $\mathcal R$ be a
certified common-refinement package whose generated carrier is the
synchronized carrier of
\autoref{thm:streamname-synchronized-window-union-carrier}. Then the
classifier row on the synchronized carrier is covered exactly by the two
restricted finite-window classifier reads together with the displayed overlap
agreement rows of $\mathcal R$.

Concretely, a synchronized classifier read is the same data as the left
restricted $\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the right
restricted $\mathsf{RatStreamNameFiniteWindowClassifier}$ row, and the common
overlap agreement on $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$,
$\mathsf{UnaryHistory}$, pointwise $\mathsf{RatHistoryClassifier}$,
$\hsame$, $\Cont$, and $\Pkg$ rows. The following $\RegSeqRat/\RealUp$
handoff reads exactly this synchronized classifier package and no row whose
value depends on whether the left or right window was used to reach the
common refinement.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-synchronized-window-union-carrier} to place the
two displayed windows over the carrier generated by $\mathcal R$. This gives
one carrier row whose visible coordinates are the restricted classifier rows,
the bundle rows, the unary-history rows, the pointwise rational-history rows,
and the $\hsame/\Cont/\Pkg$ provenance rows.

For the left-to-right reading, project the synchronized carrier back to the
two finite windows. The common-refinement source determinacy theorem,
\autoref{thm:streamname-common-refinement-source-determinacy}, identifies the
source tuple used by each restriction, and
\autoref{thm:streamname-common-refinement-source-confluence} identifies the
two routes through the overlap ledger. Hence every synchronized classifier
coordinate is read as one of the two restricted classifier rows or as an
overlap agreement row.

For the converse reading, start with the two restricted finite-window
classifier rows and the displayed overlap agreement rows. Determinacy fixes
the common source tuple, confluence identifies the two overlap routes, and the
carrier theorem repacks the rows as a single synchronized classifier package.

Finally apply \autoref{thm:streamname-synchronized-window-regseqrat-seal}.
The downstream $\RegSeqRat/\RealUp$ boundary reads the synchronized classifier
package just constructed, so no additional route-dependent row remains for the
handoff.
\end{proof}

\begin{theorem}[StreamName window-union associativity]
\label{thm:streamname-window-union-associativity}
Let $\mathcal W_0$, $\mathcal W_1$, and $\mathcal W_2$ be three composable
synchronized finite observation windows over the same accepted
$\StreamNameUp$ packet. Suppose the displayed common-refinement rows make the
left pair, the right pair, and the two iterated synchronized windows use the
same finite observation rows, $\hsame$ transports, $\Cont$ routes, and $\Pkg$
provenance. Then the carrier package obtained by first unioning
$\mathcal W_0$ with $\mathcal W_1$ and then unioning the result with
$\mathcal W_2$ classifies together with the carrier package obtained by first
unioning $\mathcal W_1$ with $\mathcal W_2$ and then unioning
$\mathcal W_0$ with the result.

The common classifier is the displayed finite observation package over the
same $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
pointwise $\mathsf{RatHistoryClassifier}$, $\hsame$, $\Cont$, and $\Pkg$ rows;
neither bracketing contributes an additional route to the
$\RegSeqRat/\RealUp$ window assembly.
\end{theorem}
\begin{proof}
First project \autoref{thm:streamname-synchronized-window-union-carrier} to the
left pair and to the right pair. Both binary unions are displayed over the
same accepted StreamName packet and the same common-refinement source rows, so
their visible carrier coordinates are the finite observation rows named in the
statement.

Project the carrier-union theorem again for the two iterated unions. The
outer union on each bracketing only repacks the already displayed
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
pointwise classifier, $\hsame$, $\Cont$, and $\Pkg$ rows.

Next apply
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. The
classifier on either iterated carrier is exhausted by the same restricted
finite-window classifier reads together with the same displayed overlap
agreement rows. Thus the two bracketings classify the identical displayed
observations.

Finally use
\autoref{thm:streamname-synchronized-window-tail-subwindow} and
\autoref{thm:streamname-synchronized-window-terminal-source-exhaustion}. Tail
restriction preserves the listed finite rows, and the terminal source boundary
has no coordinate for an extra observation route, quotient stream, completion
object, host function, or host real equality.
\end{proof}

\begin{theorem}[StreamName synchronized-window selected-tail exhaustion]
\label{thm:streamname-synchronized-window-selected-tail-exhaustion}
Let $\mathcal W_L$ and $\mathcal W_R$ be synchronized finite
$\StreamNameUp$ windows over maps $s,t$, and let the common carrier and
classifier rows satisfy
\autoref{thm:streamname-synchronized-window-union-carrier} and
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. For
any accepted $\RegSeqRat$ spine read from this synchronized surface, the
selected tail surface consumed by the finite $\RealUp$ seal is exhausted by
the displayed $\mathsf{ProbeBundle}$ rows, $\mathsf{InBundle}$ membership
rows, $\mathsf{UnaryHistory}$ rows, pointwise
$\mathsf{RatHistoryClassifier}$ rows, $\DyadicRatCore$ endpoint and radius
rows, $\hsame$, $\Cont$, $\Pkg$, and the finite $\mathsf{RealLedgerPolicy}$
rows.

No host index equality, quotient stream, completion object, host function,
Classical datum, or host real equality is introduced by this selected-tail
read.
\end{theorem}
\begin{proof}
Begin with the synchronized carrier theorem. It identifies the left and right
finite StreamName windows over one displayed common-refinement carrier and
lists the bundle, membership, unary-history, pointwise rational-history,
$\hsame$, $\Cont$, and $\Pkg$ rows visible on that carrier.

Next apply the classifier coverage theorem. The classifier read used by the
accepted $\RegSeqRat$ spine is therefore the synchronized classifier package,
not a route-dependent copy from either original window.

Now use the RegSeqRat seal handoff from
\autoref{thm:streamname-synchronized-window-regseqrat-seal} together with the
terminal cover gluing in
\autoref{thm:streamname-regseqrat-realup-source-boundary-exhaustion}. These
two results identify the accepted spine's endpoint, radius, regularity, and
readback rows with the finite $\DyadicRatCore$ and $\mathsf{RealLedgerPolicy}$
rows consumed by the $\RealUp$ seal.

The listed rows are exactly the selected-tail coordinates available to the
seal consumer. Since neither the synchronized carrier nor the RegSeqRat
handoff has coordinates for host index equality, quotient streams, completion
objects, host functions, Classical data, or host real equality, no such row can
be read at the terminal boundary.
\end{proof}

\begin{theorem}[StreamName synchronized-window terminal source exhaustion]
\label{thm:streamname-synchronized-window-terminal-source-exhaustion}
Let $\mathcal S$ be a synchronized finite $\StreamNameUp$ row whose
downstream $\RegSeqRat$ handoff and finite-window $\RealUp$ terminal seal are
read through the carrier of
\autoref{thm:streamname-synchronized-window-union-carrier} and the classifier
coverage of
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. Then
every source row visible to the terminal $\RegSeqRat/\RealUp$ consumer is one
of the following displayed finite BEDC rows: the synchronized
$\StreamNameUp$ classifier rows, the selected $\mathsf{ProbeBundle}$ rows,
the $\mathsf{InBundle}$ membership rows, the $\mathsf{UnaryHistory}$ rows,
the pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted
$\RegSeqRat$ endpoint, radius, regularity, and readback rows, the
$\DyadicRatCore$ endpoint rows, and the displayed $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ provenance rows.

The terminal consumer has no coordinate from which to read quotient streams,
host-index equality, hidden stream rows, independent regularity witnesses,
completion objects, standard bridge rows, or real-completeness principles.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-synchronized-window-union-carrier}. It gives a
single synchronized carrier whose visible source coordinates are the finite
classifier, bundle, membership, unary-history, pointwise rational-history,
and $\hsame/\Cont/\Pkg$ rows.

Apply \autoref{thm:streamname-synchronized-window-union-classifier-coverage}.
This identifies every synchronized classifier read with the two restricted
finite-window classifier reads and the displayed overlap agreement rows, so
the classifier contributes no hidden stream coordinate.

Apply \autoref{thm:streamname-synchronized-window-regseqrat-seal}. The
accepted $\RegSeqRat$ handoff supplies exactly the endpoint, radius,
regularity, readback, DyadicRatCore endpoint, and finite $\RealUp$ seal rows
consumed downstream.

It remains to exclude extra sources at the terminal face. The no-extra
coordinate clause of
\autoref{thm:streamname-synchronized-window-namecert-boundary} removes
quotient streams, host-index equality, hidden stream rows, independent
regularity witnesses, completion objects, standard bridge rows, and
real-completeness principles from the consumer boundary.
\end{proof}

\begin{theorem}[StreamName synchronized-window tail-subwindow stability]
\label{thm:streamname-synchronized-window-tail-subwindow}
Let $\mathcal S$ be a synchronized finite $\StreamNameUp$ row whose carrier and
classifier coverage are the rows of
\autoref{thm:streamname-synchronized-window-union-carrier} and
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. For
any certified finite tail subwindow of $\mathcal S$, restriction preserves the
same $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
pointwise $\mathsf{RatHistoryClassifier}$, $\DyadicRatCore$, $\RegSeqRat$,
$\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows visible at the
terminal consumer.

The restricted terminal consumer has no added coordinate for quotient streams,
host-index equality, completion objects, host functions, Classical data, or
host real equality.
\end{theorem}
\begin{proof}
Project the synchronized carrier row given by
\autoref{thm:streamname-synchronized-window-union-carrier}. Its finite carrier
coordinates are the displayed probe-bundle membership, unary observation,
classifier, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so a certified
tail subwindow is obtained by restricting those visible finite coordinates.

Apply the classifier coverage of
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. The
pointwise rational-history rows remain attached to the restricted unary
observations because coverage is stated over the synchronized finite rows and
their overlap agreement, not over a host stream quotient.

Use selected-tail exhaustion through
\autoref{thm:streamname-synchronized-window-regseqrat-seal}. The accepted
$\RegSeqRat$ handoff reads only the selected endpoint, radius, regularity,
readback, and $\DyadicRatCore$ endpoint rows, all of which are already among
the restricted finite coordinates.

Finally apply
\autoref{thm:streamname-synchronized-window-terminal-source-exhaustion}. The
terminal $\RegSeqRat/\RealUp$ consumer sees only the listed source rows, so the
tail subwindow exposes no quotient stream, host-index equality, completion
object, host function, Classical datum, or host real equality.
\end{proof}

\begin{theorem}[StreamName finite-observation classifier exhaustion]
\label{thm:streamname-finite-observation-classifier-exhaustion}
Let $\mathcal S$ be a synchronized finite $\StreamNameUp$ row whose
downstream $\RegSeqRat$ handoff and finite-window $\RealUp$ terminal seal are
read through the carrier of
\autoref{thm:streamname-synchronized-window-union-carrier}. For every selected
certified unary observation consumed by that handoff, the consumer-visible
classifier data factors through exactly the displayed
$\mathsf{ProbeBundle}$ row, $\mathsf{InBundle}$ membership row,
$\mathsf{UnaryHistory}$ row, pointwise
$\mathsf{RatHistoryClassifier}$ row, $\hsame$ comparison, $\Cont$ route,
$\Pkg$ provenance, and $\NameCert$ provenance of the synchronized window.

Thus the single finite observation seen by the downstream
$\RegSeqRat/\RealUp$ consumer has no coordinate for a regularity witness,
quotient stream, completion row, host index equality, or host real equality.
\end{theorem}
\begin{proof}
First project the synchronized row through
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. The
chosen certified unary observation is one member of the covered finite
classifier inventory, so its visible rows are the bundle, membership,
unary-history, pointwise rational-history, $\hsame$, $\Cont$, and $\Pkg$
coordinates of that inventory.

Next apply \autoref{thm:streamname-regseqrat-pointwise-handoff} to the chosen
observation. The pointwise handoff reads exactly the displayed StreamName
carrier and classifier rows at that observation before it reaches the
$\RegSeqRat$ or finite-window $\RealUp$ consumer.

Finally use
\autoref{thm:streamname-synchronized-window-terminal-source-exhaustion}. Its
terminal-source boundary adds the $\NameCert$ provenance row and removes
regularity witnesses, quotient streams, completion rows, host index equality,
and host real equality from the terminal consumer surface.
\end{proof}

\begin{theorem}[StreamName constant reindexing Real seal boundary]
\label{thm:streamname-constant-reindexing-real-seal-boundary}
Let $d,e:\Hist$ be rational-history endpoints, let $r,q:\Hist\to\Hist$ be
two observation schedules, and let $\mathcal S$ be the synchronized finite
$\StreamNameUp$ row built from the independently reindexed constant rational
streams $\mathsf{RatConstStream}_d\circ r$ and
$\mathsf{RatConstStream}_e\circ q$. The finite $\RealUp$ seal read from
$\mathcal S$ sees only the constant $\RatUp$ endpoint data for $d$ and $e$,
the two reindexing schedules, finite-window membership in the displayed
$\mathsf{ProbeBundle}$, certified $\mathsf{UnaryHistory}$ rows, and the
pointwise $\mathsf{RatHistoryClassifier}$ rows selected by the synchronized
classifier.

In particular, the seal does not read a quotient stream, completion object,
host real equality, host index equality, or independent regularity witness.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:rat-stream-name-independent-reindexed-constant-classifier}. It
places the two independently reindexed constant streams over the same
StreamName classifier surface and reduces every selected classifier row to
the RatUp endpoint classifier between $d$ and $e$.

Then use
\autoref{thm:rat-stream-name-independent-reindexed-constant-point-exactness}.
The carrier and classifier data of the independently reindexed constant
streams are exactly the endpoint carrier and classifier data at $d$ and $e$;
the schedules $r$ and $q$ contribute only the displayed observation routing.

Pass this synchronized constant row through
\autoref{thm:streamname-finite-observation-classifier-exhaustion}. The
finite $\RealUp$ seal therefore reads only the constant RatUp endpoint, the
reindexing schedules, the finite-window membership and unary-history rows,
and the pointwise classifier rows, with no stronger host-level coordinate.
\end{proof}

\begin{theorem}[StreamName RegSeqRat common-window terminal seal determinacy]
\label{thm:streamname-regseqrat-common-window-terminal-seal-determinacy}
Let $\mathcal S_0$ and $\mathcal S_1$ be synchronized finite
$\StreamNameUp$ rows. Suppose that they have the same common-refinement
source, the same accepted $\RegSeqRat$ spine, and the same displayed
$\DyadicRatCore$ endpoint and radius rows. If a terminal finite-window
$\RealUp$ seal is read from either synchronized route, then the two reads
produce the same consumer-facing seal row.

The determining surface is exactly the displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, $\mathsf{ProbeBundle}$
rows, $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ rows,
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, the $\DyadicRatCore$ endpoint and radius rows, and the visible
$\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and
$\mathsf{RealLedgerPolicy}$ rows. The terminal seal has no coordinate for
quotient streams, host-index equality, completion objects, independent
regularity witnesses, standard bridge rows, or real-completeness principles.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-synchronized-window-union-classifier-coverage}. It
projects both synchronized routes to the same finite classifier inventory over
the common-refinement source, with the same bundle, membership,
unary-history, pointwise rational-history, and overlap rows.

Next apply \autoref{thm:streamname-synchronized-window-regseqrat-seal}. The
accepted $\RegSeqRat$ spine and the displayed $\DyadicRatCore$ endpoint and
radius rows are therefore the only rational handoff rows available to the
terminal finite-window $\RealUp$ seal.

The source boundary is exhausted by
\autoref{thm:streamname-synchronized-window-terminal-source-exhaustion} and by
the seal boundary of
\autoref{thm:streamname-synchronized-window-namecert-boundary}. These two
boundaries leave only the displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$, $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
$\mathsf{RatHistoryClassifier}$, $\RegSeqRat$, $\DyadicRatCore$, $\hsame$,
$\Cont$, $\Pkg$, $\NameCert$, and $\mathsf{RealLedgerPolicy}$ rows.

Both routes have the same rows in that inventory by hypothesis. Since the
terminal $\RealUp$ seal has no further coordinate beyond this inventory, the
consumer-facing seal read from $\mathcal S_0$ is the same row as the seal read
from $\mathcal S_1$.
\end{proof}

\begin{theorem}[StreamName RegSeqRat uniform-tail seal confluence]
\label{thm:streamname-regseqrat-uniform-tail-seal-confluence}
Let $\mathcal S_0$, $\mathcal S_1$, and $\mathcal S_2$ be synchronized finite
$\StreamNameUp$ windows over one accepted rational stream-name schedule.
Suppose each adjacent pair admits a common-window package, and suppose all
three windows feed the same $\RegSeqRat$ handoff and the same terminal
finite-window $\RealUp$ seal rows. Then the terminal seal reads from
$\mathcal S_0$ and $\mathcal S_2$ agree on the visible endpoint, dyadic
radius, regularity ledger, classifier ledger, $\hsame$ comparisons, $\Cont$
routes, $\Pkg$ provenance, $\NameCert$ provenance, and terminal
$\mathsf{RealLedgerPolicy}$ rows.

The confluence is a finite-window statement over the displayed synchronized
ledger. It does not identify quotient streams, host-index equality, completion
objects, independent regularity witnesses, standard bridge rows, or real
completeness principles.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-synchronized-window-regseqrat-seal} to the
$\mathcal S_0/\mathcal S_1$ synchronized pair and again to the
$\mathcal S_1/\mathcal S_2$ synchronized pair. Each application exposes the
same accepted $\RegSeqRat$ handoff, endpoint row, dyadic-radius row,
regularity ledger, readback row, and terminal finite-window $\RealUp$ seal
surface carried by the common schedule.

Next use
\autoref{thm:streamname-regseqrat-common-window-terminal-seal-determinacy} on
the adjacent pairs. The first application identifies the terminal read from
$\mathcal S_0$ with the read from $\mathcal S_1$, and the second identifies
the read from $\mathcal S_1$ with the read from $\mathcal S_2$ on exactly the
visible finite inventory.

Compose these displayed row equalities by transitivity in the generated
common-window ledger. The middle window contributes no separate coordinate:
it is the shared finite $\StreamNameUp$ synchronization surface, so the first
and third terminal reads agree on the endpoint, radius, regularity,
classifier, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and
$\mathsf{RealLedgerPolicy}$ rows and on no stronger host-level object.
\end{proof}

\begin{theorem}[StreamName RegSeqRat finite-window chain compaction]
\label{thm:streamname-regseqrat-finite-window-chain-compaction}
Let
$$
\mathcal S_0,\mathcal S_1,\ldots,\mathcal S_n
$$
be a finite chain of synchronized $\StreamNameUp$ windows over one accepted
rational stream-name schedule. Suppose every adjacent pair
$\mathcal S_i,\mathcal S_{i+1}$ satisfies the common-window terminal seal
determinacy hypotheses, and suppose every window feeds the same accepted
$\RegSeqRat$ handoff. Then all terminal finite-window $\RealUp$ seal reads
through the chain compact to one seal-facing surface.

The compacted surface has exactly the shared
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, $\mathsf{ProbeBundle}$
rows, $\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ rows,
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, $\DyadicRatCore$ endpoint and radius rows, and the visible $\hsame$,
$\Cont$, $\Pkg$, $\NameCert$, and $\mathsf{RealLedgerPolicy}$ rows. It contains
no quotient stream row, host-index equality row, completion object, standard
bridge row, or real-completeness principle.
\end{theorem}
\begin{proof}
Induct on the displayed finite chain. In the first nonempty adjacent case,
\autoref{thm:streamname-regseqrat-common-window-terminal-seal-determinacy}
identifies the two terminal reads through the common synchronized window and
leaves exactly the stated StreamName, RegSeqRat, DyadicRatCore, transport,
provenance, and Real ledger rows.

For the induction step, assume the initial segment has already compacted to one
terminal seal-facing surface. The next adjacent pair satisfies the same
determinacy hypotheses, so
\autoref{thm:streamname-regseqrat-common-window-terminal-seal-determinacy}
identifies the last read of the compacted segment with the read of the new
window.

Apply \autoref{thm:streamname-regseqrat-uniform-tail-seal-confluence} to compose
the compacted segment, the shared middle window, and the new terminal window.
The confluence theorem keeps the accepted $\RegSeqRat$ handoff and every
visible row on the same synchronized schedule, so the enlarged chain again has
one terminal finite-window $\RealUp$ seal surface.

At no step is there a coordinate from which to read quotient streams,
host-index equality, completion objects, standard bridge data, or real
completeness. The induction therefore compacts the whole finite chain to the
single displayed terminal seal inventory.
\end{proof}
