\section{StreamName Tail-Window Coverage Packet}
\label{sec:streamname-tail-window-coverage-packet}

\begin{definition}[StreamName tail-window coverage packet]
\label{def:streamname-tail-window-coverage-packet}
A StreamName tail-window coverage packet for a selected finite $\RealUp$
consumer window is the finite ledger consisting exactly of these rows:
\begin{enumerate}
\item a displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$ row for public
$\StreamNameUp$ rational stream endpoints $s,t:\mathsf{BHist}\to\mathsf{BHist}$
and the selected finite $\mathsf{ProbeBundle}$ window $\mathcal P$;
\item for each selected observation $n$, the bundled
$\mathsf{UnaryHistory}(n)$ and $\mathsf{InBundle}(n,\mathcal P)$ rows;
\item the pointwise $\mathsf{RatHistoryClassifier}(s(n),t(n))$ row read from
the selected StreamName observation;
\item the accepted $\RegSeqRat$ spine selected by the pointwise rational-history
rows and by the finite-window handoff;
\item the selected finite $\RealUp$ windows whose DyadicRatCore endpoint rows
are read from that accepted $\RegSeqRat$ spine; and
\item the shared $\Cont$, $\hsame$, $\Pkg$, and
$\mathsf{RealLedgerPolicy}$ rows joining the StreamName endpoints, the accepted
$\RegSeqRat$ spine, the DyadicRatCore endpoint rows, and the selected $\RealUp$
readback packets.
\end{enumerate}

The packet is only this displayed finite ledger. It contains no completion
object, quotient representative, host-index equality, metric-completeness row,
arithmetic or order operation, standard bridge row, or hidden selector.
\end{definition}

\begin{theorem}[StreamName tail-window coverage exhaustion]
\label{thm:streamname-tail-window-coverage-exhaustion}
Every consumer row of a StreamName tail-window coverage packet is one of the
rows displayed in \autoref{def:streamname-tail-window-coverage-packet}. In
particular, the consumer can read only the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the bundled
$\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine, the
selected DyadicRatCore endpoint rows, and the shared
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-tail-selector-handoff-exactness}. It
decomposes the handoff exported across the Real-and-Completion boundary into
the StreamName finite-window classifier, selected unary observations, bundle
membership, pointwise rational-history classifiers, the accepted $\RegSeqRat$
spine, and the finite $\RealUp$ ledger.

Next apply
\autoref{thm:streamname-regseqrat-tail-selector-real-window-factorization} to
the selected $\RealUp$ window. This says every consumer-facing $\RealUp$ row
factors through the same displayed finite public surface and through no
additional selector row.

Combining the two exactness statements gives the exhaustion claim. Any row
read by the consumer is already named by the coverage packet, and every row
excluded by the two cited theorems remains outside the packet boundary.
\end{proof}

\begin{theorem}[RegSeqRat finite-window classifier coverage]
\label{thm:streamname-regseqrat-finite-window-classifier-coverage}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
rational stream endpoints, let $\mathcal P$ be a finite
$\mathsf{ProbeBundle}$ window, and suppose a StreamName tail-window coverage
packet displays the row
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$. For every
certified observation $n$ with $\mathsf{UnaryHistory}(n)$ and
$\mathsf{InBundle}(n,\mathcal P)$, the pointwise row
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ is exposed in the same packet. The
accepted $\RegSeqRat$ spine consumes exactly these exposed pointwise
rational-history classifier rows, together with their displayed unary-history
and bundle-membership witnesses.

No completion object, quotient representative, host-index equality,
$\RealUp$ seal classifier, metric-completeness row, arithmetic or order row,
or standard bridge row is supplied by this coverage claim.
\end{theorem}
\begin{proof}
Unfold \autoref{def:streamname-tail-window-coverage-packet}. The packet
contains the finite-window classifier row, the bundled
$\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows, and the pointwise
$\mathsf{RatHistoryClassifier}$ rows read from the selected StreamName
observations.

Project the component indexed by the certified observation $n$. The hypotheses
$\mathsf{UnaryHistory}(n)$ and $\mathsf{InBundle}(n,\mathcal P)$ identify $n$
as one of the selected observations of the displayed finite window, so the
corresponding pointwise rational-history classifier is precisely
$\mathsf{RatHistoryClassifier}(s(n),t(n))$.

The accepted $\RegSeqRat$ spine is then the spine named in the same packet from
these pointwise rows and the finite-window handoff. Apply
\autoref{thm:streamname-tail-window-coverage-exhaustion} to rule out any
additional consumer row.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. The
$\RealUp$ readback can use only the finite windows selected from the accepted
spine, while completion, quotient, host-index equality, seal classifier,
metric-completeness, arithmetic or order, and standard bridge rows remain
outside the packet boundary.
\end{proof}

\begin{theorem}[StreamName tail-window dyadic endpoint determinacy]
\label{thm:streamname-tail-window-dyadic-endpoint-determinacy}
Let $\mathcal P$ and $\mathcal Q$ be StreamName tail-window coverage packets
over shared public endpoints $s,t:\mathsf{BHist}\to\mathsf{BHist}$ and the same
accepted $\RegSeqRat$ spine. Suppose their displayed finite-window classifier
rows agree, and suppose the selected $\mathsf{UnaryHistory}$ and
$\mathsf{InBundle}$ membership rows agree by the shown
$\hsame/\Cont/\Pkg$ provenance. Then the two packets expose identical
DyadicRatCore endpoint rows to any finite $\RealUp$ consumer.

The determined finite interface is the shared
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the selected
$\mathsf{ProbeBundle}/\mathsf{InBundle}/\mathsf{UnaryHistory}$ rows, the
pointwise $\mathsf{RatHistoryClassifier}$ rows consumed by the accepted
$\RegSeqRat$ spine, the DyadicRatCore endpoint rows, and the common
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger. It contains no completion,
quotient, metric-completeness, arithmetic or order, or standard-bridge row.
\end{theorem}
\begin{proof}
Unfold \autoref{def:streamname-tail-window-coverage-packet}. The only selected
rows available for comparison are the finite-window classifier, the displayed
bundle and unary-history rows, the pointwise rational-history classifiers, the
accepted $\RegSeqRat$ spine, the DyadicRatCore endpoint rows, and the finite
ledger provenance.

Apply \autoref{thm:streamname-regseqrat-finite-window-classifier-coverage}. The
shared finite-window classifier and the agreed selected membership rows force
the same pointwise $\mathsf{RatHistoryClassifier}$ rows to feed the common
accepted $\RegSeqRat$ spine in both packets.

Next apply \autoref{thm:streamname-tail-window-coverage-exhaustion}. Since the
accepted spine and its pointwise StreamName inputs are the same displayed rows,
the DyadicRatCore endpoint rows selected from that spine are the same finite
packet rows for both consumers.

Finally use \autoref{thm:streamname-tail-window-realup-boundary}. The boundary
has no slot for completion, quotient, metric-completeness, arithmetic or order,
or standard bridge data, so no off-packet row can separate the two exposed
DyadicRatCore endpoint surfaces.
\end{proof}

\begin{theorem}[StreamName tail-window hsame transport stability]
\label{thm:streamname-tail-window-hsame-transport-stability}
Let $\mathcal P$ be a StreamName tail-window coverage packet over public
endpoints $s,t:\mathsf{BHist}\to\mathsf{BHist}$. Suppose the displayed
$\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows transport componentwise the
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\mathcal P)$ row, the
selected $\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows, each pointwise
$\mathsf{RatHistoryClassifier}$ row, the accepted $\RegSeqRat$ spine, the
DyadicRatCore endpoint rows, and the $\mathsf{RealLedgerPolicy}$ ledger to a
second displayed finite window. Then the transported rows form another
StreamName tail-window coverage packet.

Moreover, every finite $\RealUp$ consumer row of the original packet
transports through the same displayed packet surface: its source is still the
finite-window classifier, selected unary and bundle rows, pointwise rational
history rows, accepted $\RegSeqRat$ spine, DyadicRatCore endpoint rows, and
shared $\Cont/\hsame/\mathsf{Pkg}/\mathsf{RealLedgerPolicy}$ ledger. The
transport supplies no completion object, quotient row, host-index equality,
metric-completeness row, arithmetic or order row, or standard bridge row.
\end{theorem}
\begin{proof}
Unfold \autoref{def:streamname-tail-window-coverage-packet}. Each row named in
the packet definition has a displayed transported partner by hypothesis: the
finite-window classifier, selected unary-history and bundle-membership rows,
pointwise rational-history rows, accepted rational-sequence spine, endpoint
readbacks, and ledger-policy rows.

Repack those transported partners in the same order. The classifier and
membership rows still select a finite StreamName window; the pointwise
rational-history rows still feed the accepted $\RegSeqRat$ spine; and the
DyadicRatCore endpoint rows and ledger rows still give the finite $\RealUp$
readback surface.

Apply \autoref{thm:streamname-tail-window-coverage-exhaustion} to the original
and transported packets. Every consumer row is one of the rows just transported,
so the consumer transport factors through exactly the same displayed packet
surface.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. Completion,
quotient, host-index equality, metric-completeness, arithmetic or order, and
standard bridge rows have no constructor in either finite packet, so the
transport cannot introduce any such row.
\end{proof}

\begin{theorem}[StreamName tail-window common refinement]
\label{thm:streamname-tail-window-cover-common-refinement}
Given two StreamName tail-window coverage packets for finite
$\mathsf{ProbeBundle}$ windows $\mathcal P$ and $\mathcal Q$ over the same
public $\StreamNameUp$ endpoints $s,t:\mathsf{BHist}\to\mathsf{BHist}$ and the
same accepted $\RegSeqRat$ spine, there is a finite coverage packet over the
bundle generated by the selected observations of $\mathcal P$ and $\mathcal Q$.
Its restrictions to the two selected subbundles recover the original packets.
Every readable row in the common packet remains one of the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the shared $\RegSeqRat$ spine, the
DyadicRatCore endpoint rows, and the shared
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ rows.
\end{theorem}
\begin{proof}
Unpack the two coverage packets using
\autoref{def:streamname-tail-window-coverage-packet}. The public endpoints
$s,t$ and the accepted $\RegSeqRat$ spine are shared, so the pointwise
rational-history classifier rows and the endpoint readback rows are compared
inside one displayed ledger.

Form the generated finite bundle by taking the selected
$\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows from $\mathcal P$ and
$\mathcal Q$ and closing under the displayed finite bundle constructor. The
restriction to each selected subbundle forgets the other selected rows and
therefore recovers the corresponding original packet.

Now apply
\autoref{thm:streamname-tail-window-coverage-exhaustion}. The generated packet
has no constructor beyond the rows named in the coverage definition, so the
union operation introduces no extra consumer row.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary} to the
generated packet and to its two restrictions. The completion, quotient,
host-index equality, metric-completeness, arithmetic or order, and standard
bridge rows remain outside all three packet boundaries.
\end{proof}

\begin{theorem}[StreamName tail-window refinement associativity]
\label{thm:streamname-tail-window-refinement-associativity}
Let $\mathcal P$, $\mathcal Q$, and $\mathcal R$ be finite
$\mathsf{ProbeBundle}$ windows carrying StreamName tail-window coverage
packets over the same public endpoints
$s,t:\mathsf{BHist}\to\mathsf{BHist}$ and the same accepted $\RegSeqRat$
spine. The common-refinement packet obtained by first refining
$(\mathcal P,\mathcal Q)$ and then refining the result with $\mathcal R$ has
the same public restriction on every selected subwindow as the packet obtained
by first refining $(\mathcal Q,\mathcal R)$ and then refining the result with
$\mathcal P$.

The shared public restriction consists exactly of the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the selected
$\mathsf{UnaryHistory}$ rows, the $\mathsf{InBundle}$ membership rows, the
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, the DyadicRatCore endpoint rows, and the shared
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-tail-window-cover-common-refinement} to
$\mathcal P$ and $\mathcal Q$, and then apply it again to the resulting
generated bundle and $\mathcal R$. This constructs the left-grouped coverage
packet with public endpoints $s,t$ and with the fixed accepted $\RegSeqRat$
spine.

Apply the same theorem to $\mathcal Q$ and $\mathcal R$, and then to
$\mathcal P$ and the resulting generated bundle. This constructs the
right-grouped coverage packet with the same endpoints and the same accepted
spine.

The finite bundle generated by selected observations is associative: selecting
the rows of $\mathcal P$ and $\mathcal Q$ and then adjoining the rows of
$\mathcal R$ gives the same selected observation family as selecting the rows
of $\mathcal Q$ and $\mathcal R$ and then adjoining the rows of $\mathcal P$.
Restriction to any chosen subwindow therefore forgets the same complement in
both grouped packets.

Now apply
\autoref{thm:streamname-tail-window-coverage-exhaustion} to both grouped
packets. Every readable row in either packet is one of the displayed
finite-window classifier, unary-history, bundle-membership,
rational-history, $\RegSeqRat$, DyadicRatCore, continuation, history,
package, or ledger-policy rows, and those rows are indexed by the same
selected observation family.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary} to both
grouped packets and to their selected restrictions. Completion, quotient,
host-index equality, metric-completeness, arithmetic or order, standard
bridge, and unexposed selector data have no constructor in either public
surface. Hence the two grouped common-refinement packets restrict to the same
public rows on every selected subwindow.
\end{proof}

\begin{theorem}[StreamName tail-window RealUp boundary]
\label{thm:streamname-tail-window-realup-boundary}
A finite $\RealUp$ consumer of a StreamName tail-window coverage packet reads
only the displayed StreamName, $\RegSeqRat$, DyadicRatCore, $\Cont$, $\hsame$,
$\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows. It reads no completion row,
quotient row, host-index equality, metric-completeness row, arithmetic or
order operation, or standard bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.StreamNameTailWindowRealUpBoundary}
\begin{proof}
Read the consumer through
\autoref{thm:streamname-tail-window-coverage-exhaustion}. The exhaustion
surface lists every available consumer row and identifies it with the finite
packet of \autoref{def:streamname-tail-window-coverage-packet}.

Now inspect the packet definition. Its StreamName side is the finite-window
classifier together with selected unary-history and bundle-membership rows.
Its rational-sequence side is the accepted $\RegSeqRat$ spine selected by the
pointwise rational-history classifiers. Its $\RealUp$ side is only the
DyadicRatCore endpoint readback and the shared
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger.

The excluded objects have no constructor in this finite ledger. Hence a
finite $\RealUp$ consumer cannot read completion, quotient, host-index
equality, metric-completeness, arithmetic or order, or standard bridge data
from the packet.
\end{proof}

\begin{theorem}[StreamName tail-window terminal consumer factorization]
\label{thm:streamname-tail-window-terminal-consumer-factorization}
Every finite $\RealUp$ consumer row whose source reads a StreamName
tail-window coverage packet factors through the displayed rows of
\autoref{def:streamname-tail-window-coverage-packet}: the
$\StreamNameUp$ finite-window classifier, the selected
$\mathsf{UnaryHistory}$ observations and $\mathsf{InBundle}$ membership rows,
the pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted
$\RegSeqRat$ spine, the DyadicRatCore observation rows, and the shared
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger. If two such consumers
are given the same displayed packet, then they have the same finite read
surface. They do not read any completion object, quotient row, host sequence
equality, or standard real-number structure.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-tail-window-coverage-exhaustion}. It enumerates
all readable rows of the packet and identifies each one with a row already
displayed in \autoref{def:streamname-tail-window-coverage-packet}.

Next apply \autoref{thm:streamname-tail-window-realup-boundary}. The finite
$\RealUp$ consumer can therefore see only the StreamName classifier,
selected unary observation and bundle rows, rational-history classifier rows,
accepted $\RegSeqRat$ spine, DyadicRatCore endpoint rows, and shared ledger
rows named in the statement.

For two consumers using the same displayed packet, apply
\autoref{thm:streamname-tail-window-cover-common-refinement} to place their
selected finite windows in one common packet. Then apply
\autoref{thm:streamname-tail-window-refinement-associativity} to see that
changing the grouping of those finite windows leaves the restriction to each
selected subwindow unchanged.

Thus the factorization is terminal among finite packet readers: every
observable row is already in the displayed packet, and any grouped finite
read of the same packet restricts back to the same StreamName, $\RegSeqRat$,
DyadicRatCore, continuation, history, package, and ledger-policy surface. The
objects excluded by the boundary theorem have no row in the factorization.
\end{proof}

\begin{theorem}[StreamName tail-window terminal source uniqueness]
\label{thm:streamname-tail-window-terminal-source-uniqueness}
Let two finite $\RealUp$ consumers read StreamName tail-window coverage packets
over the same public $\StreamNameUp$ endpoints
$s,t:\mathsf{BHist}\to\mathsf{BHist}$ and the same accepted $\RegSeqRat$
spine. If a common-refinement packet restricts to both packets, then both
consumers factor through the same displayed StreamName, $\RegSeqRat$,
DyadicRatCore, $\Cont$, $\hsame$, $\Pkg$, and
$\mathsf{RealLedgerPolicy}$ source surface. No alternative $\RealUp$ source
row, quotient representative, completion row, or host-index equality can be
read from either finite consumer.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-tail-window-cover-common-refinement}.
The two selected finite windows sit in one coverage packet over the shared
public StreamName endpoints and the shared accepted $\RegSeqRat$ spine, and
the restrictions to the selected subwindows recover the two original packets.

Next apply \autoref{thm:streamname-tail-window-refinement-associativity}.
Any regrouping of the common finite window has the same public restriction on
each selected subwindow, so the two consumers see the same StreamName
finite-window classifier rows, selected unary-history and bundle-membership
rows, pointwise rational-history classifier rows, accepted $\RegSeqRat$
spine, DyadicRatCore endpoint rows, and shared ledger rows.

Now apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization}. Every
finite $\RealUp$ consumer row factors through exactly that displayed packet
surface, and two consumers reading the same restricted packet have the same
finite read surface.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. The
boundary removes completion, quotient, host-index equality,
metric-completeness, arithmetic or order, standard bridge, and hidden
selector data from the readable packet. Hence no other $\RealUp$ source row,
quotient representative, completion row, or host-index equality can be read,
and the displayed StreamName/$\RegSeqRat$/DyadicRatCore source surface is the
unique finite source surface for both consumers.
\end{proof}

\begin{theorem}[StreamName tail-window global classifier boundary]
\label{thm:streamname-tail-window-global-classifier-boundary}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints. Suppose that every certified unary observation singleton window
over the endpoints carries the row
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,\Bcons(n,\Bnil))$. If a
finite $\RealUp$ consumer reads a StreamName tail-window coverage packet
generated from finitely many selected observations over an accepted
$\RegSeqRat$ spine, then the consumer factors through the global
$\mathsf{RatStreamNameClassifier}(s,t)$ together with exactly the displayed
StreamName, $\RegSeqRat$, DyadicRatCore, $\Cont$, $\hsame$, $\Pkg$, and
$\mathsf{RealLedgerPolicy}$ packet surface.

The factorization exposes no completion object, quotient representative,
host-index equality, metric-completeness row, arithmetic or order operation,
or standard bridge row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:rat-stream-name-finite-window-exhausts-classifier}. The
singleton-window hypotheses exhaust the certified finite observations and
therefore determine the global
$\mathsf{RatStreamNameClassifier}(s,t)$ for the public StreamName endpoints.

Next apply \autoref{thm:streamname-tail-window-coverage-exhaustion}. The
finite packet read by the $\RealUp$ consumer has only the enumerated selected
unary-history rows, bundle-membership rows, pointwise rational-history
classifier rows, accepted $\RegSeqRat$ spine, DyadicRatCore endpoint rows,
and shared $\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ ledger.

Now apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization}. Every
finite consumer row factors through that displayed packet surface, so the
global classifier supplied by the singleton-window exhaustion is the only
StreamName classifier row available to the consumer.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. The
boundary excludes completion, quotient representatives, host-index equality,
metric-completeness, arithmetic and order operations, and standard bridge
data. Hence the finite $\RealUp$ consumer factors through the global
StreamName classifier and the displayed packet rows, with no off-boundary row
exposed.
\end{proof}

\begin{theorem}[StreamName tail-window global classifier transport stability]
\label{thm:streamname-tail-window-global-classifier-transport-stability}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints satisfying the singleton-window hypotheses of
\autoref{thm:streamname-tail-window-global-classifier-boundary}. Let
$\mathcal P$ be a StreamName tail-window coverage packet over $s,t$, generated
from finitely many selected observations over an accepted $\RegSeqRat$ spine.
Suppose displayed $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows transport
$s,t$ and every row of $\mathcal P$ to endpoints $s',t'$ and to a second
finite tail-window coverage packet $\mathcal P'$ over the transported
endpoints.

Then every finite $\RealUp$ consumer of $\mathcal P'$ factors through the
transported global
$\mathsf{RatStreamNameClassifier}(s',t')$ and exactly the transported
StreamName, $\RegSeqRat$, DyadicRatCore, $\Cont$, $\hsame$, $\mathsf{Pkg}$,
and $\mathsf{RealLedgerPolicy}$ packet surface. The transported consumer
reads no completion object, quotient representative, host-index equality,
metric-completeness row, arithmetic or order operation, or standard bridge
row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-tail-window-hsame-transport-stability}. The displayed
$\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows carry the finite-window classifier,
selected unary-history and bundle-membership rows, pointwise
rational-history classifiers, accepted $\RegSeqRat$ spine, DyadicRatCore
endpoint rows, and ledger-policy rows into the transported packet
$\mathcal P'$.

The singleton-window hypotheses transport with those same displayed rows.
Apply \autoref{thm:streamname-tail-window-global-classifier-boundary} to
$\mathcal P'$ over $s',t'$. This supplies the transported global
$\mathsf{RatStreamNameClassifier}(s',t')$ as the StreamName classifier row
available to any finite $\RealUp$ consumer of the transported packet.

Now apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization}. The
consumer factors through the transported packet surface: the StreamName
classifier rows, selected window rows, pointwise rational-history rows,
accepted rational-sequence spine, DyadicRatCore endpoint rows, continuation
rows, history comparisons, package provenance, and ledger policy.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. Since the
transported finite packet has no constructor for completion, quotient,
host-index equality, metric-completeness, arithmetic or order, or standard
bridge rows, none of those rows can be read by the transported consumer.
\end{proof}

\begin{theorem}[StreamName tail-window selected pointwise transport]
\label{thm:streamname-tail-window-selected-pointwise-transport}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints, and let $\mathcal P$ be a StreamName tail-window coverage packet
over a finite $\mathsf{ProbeBundle}$. Suppose a selected unary observation row
$\mathsf{InBundle}(n,\mathcal P)$ carries the pointwise classifier
$\mathsf{RatHistoryClassifier}(s(n),t(n))$. If the displayed $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ rows transport that selected observation to a
selected row in a transported finite packet $\mathcal P'$, then the
transported pointwise classifier row remains one of the visible rows of
$\mathcal P'$.

Every finite $\RealUp$ consumer using that selected observation factors
through the transported StreamName/$\RegSeqRat$/DyadicRatCore packet surface.
No completion, quotient, host-index equality, metric-completeness,
arithmetic or order row, or standard-bridge row is exposed.
\end{theorem}
\begin{proof}
First unfold the StreamName tail-window coverage packet of
\autoref{def:streamname-tail-window-coverage-packet}. The selected
$\mathsf{InBundle}(n,\mathcal P)$ row is one of the finite packet coordinates,
together with its unary-history row and pointwise
$\mathsf{RatHistoryClassifier}(s(n),t(n))$ row.

Apply \autoref{thm:streamname-tail-window-hsame-transport-stability}. The
displayed $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows repack the selected
observation, its bundle-membership row, and its pointwise classifier into the
transported packet $\mathcal P'$ over the transported endpoints.

Next apply \autoref{thm:streamname-tail-window-coverage-exhaustion} to
$\mathcal P'$. The exhaustion statement enumerates the transported selected
unary-history rows, bundle-membership rows, and pointwise rational-history
classifier rows, so the transported classifier attached to $n$ is a visible
row of $\mathcal P'$.

Finally apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization} and
\autoref{thm:streamname-tail-window-realup-boundary}. Any finite $\RealUp$
consumer using the selected row factors through the transported StreamName,
$\RegSeqRat$, DyadicRatCore, $\Cont$, $\hsame$, $\mathsf{Pkg}$, and ledger
surface, and the boundary has no coordinate for completion, quotient,
host-index equality, metric-completeness, arithmetic or order, or a standard
bridge.
\end{proof}

\begin{theorem}[StreamName selected transport coverage]
\label{thm:streamname-tail-window-selected-transport-coverage}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints, let $\mathcal P$ be a StreamName tail-window coverage packet over a
finite $\mathsf{ProbeBundle}$, and let $\mathcal P'$ be the transported packet
obtained from displayed $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows. Suppose the
selected observations of $\mathcal P$ are transported to selected observations
of $\mathcal P'$ by those displayed rows.

Then every transported selected pointwise
$\mathsf{RatHistoryClassifier}$ row, accepted $\RegSeqRat$ spine row,
DyadicRatCore endpoint row, and finite $\RealUp$ consumer row factors through
the transported tail-window coverage packet $\mathcal P'$. The factorization
uses only the transported StreamName, $\RegSeqRat$, DyadicRatCore, $\Cont$,
$\hsame$, $\mathsf{Pkg}$, and $\mathsf{RealLedgerPolicy}$ rows. It exposes no
completion object, quotient representative, host-index equality,
metric-completeness row, arithmetic or order operation, or standard bridge row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-tail-window-selected-pointwise-transport} to each
selected observation. The transported selected rows remain visible coordinates
of $\mathcal P'$, together with their pointwise
$\mathsf{RatHistoryClassifier}$ rows.

Next apply
\autoref{thm:streamname-tail-window-global-classifier-transport-stability}. The
transported packet supplies the global
$\mathsf{RatStreamNameClassifier}$ row and preserves the accepted
$\RegSeqRat$ spine and DyadicRatCore endpoint rows through the displayed
$\hsame$, $\Cont$, and $\mathsf{Pkg}$ routes.

Finally apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization} and
\autoref{thm:streamname-tail-window-realup-boundary}. Every finite $\RealUp$
consumer of the transported packet factors through the listed packet rows, and
the boundary theorem rules out completion objects, quotient representatives,
host-index equality, metric-completeness rows, arithmetic or order operations,
and standard bridge rows.
\end{proof}

\begin{theorem}[StreamName tail-window RegSeqRat coverage lock]
\label{thm:streamname-tail-window-regseqrat-coverage-lock}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints, and let $\mathcal P$ and $\mathcal Q$ be StreamName tail-window
coverage packets over finite windows. Suppose their displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, selected
$\mathsf{UnaryHistory}$ rows, selected $\mathsf{InBundle}$ rows, pointwise
$\mathsf{RatHistoryClassifier}$ rows, accepted $\RegSeqRat$ spine,
DyadicRatCore endpoint rows, and $\Cont/\hsame/\mathsf{Pkg}/
\mathsf{RealLedgerPolicy}$ provenance rows agree through the transported
packet surface.

Then every finite $\RealUp$ consumer of $\mathcal P$ and every finite
$\RealUp$ consumer of $\mathcal Q$ read the same DyadicRatCore endpoint rows
and the same finite ledger rows from that shared $\RegSeqRat$ spine. This
lock exposes no completion data, quotient representative, host-index
equality, metric-completeness row, arithmetic or order operation, or standard
bridge row.
\end{theorem}
\begin{proof}
Unfold the StreamName tail-window coverage packet of
\autoref{def:streamname-tail-window-coverage-packet} for both
$\mathcal P$ and $\mathcal Q$. Apply
\autoref{thm:streamname-tail-window-coverage-exhaustion} to each packet. The
only finite source rows available on either side are the displayed
finite-window classifier rows, selected unary-history and bundle-membership
rows, pointwise rational-history classifier rows, accepted $\RegSeqRat$
spine, DyadicRatCore endpoints, and ledger provenance.

Next apply
\autoref{thm:streamname-tail-window-global-classifier-transport-stability}
and \autoref{thm:streamname-tail-window-selected-transport-coverage}. The
hypothesized transported packet surface identifies the selected rows of
$\mathcal P$ with the selected rows of $\mathcal Q$ and carries their
accepted rational-sequence spine and DyadicRatCore endpoint rows through the
same $\Cont$, $\hsame$, $\mathsf{Pkg}$, and
$\mathsf{RealLedgerPolicy}$ routes.

Now apply
\autoref{thm:streamname-tail-window-terminal-source-uniqueness}. Since the
two finite packets restrict to the same transported selected source surface,
their finite $\RealUp$ consumers have the same displayed
StreamName/$\RegSeqRat$/DyadicRatCore source surface and the same finite
continuation ledger.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. The
boundary theorem removes completion data, quotient representatives,
host-index equality, metric-completeness rows, arithmetic or order
operations, and standard bridge rows from every finite consumer. Thus the
only endpoint and ledger rows read by either consumer are the common
DyadicRatCore endpoint rows and the common ledger rows carried by the shared
$\RegSeqRat$ spine.
\end{proof}

\begin{theorem}[StreamName tail-window prefix-suffix recomposition]
\label{thm:streamname-tail-window-prefix-suffix-recomposition}
Let $s,t:\mathsf{BHist}\to\mathsf{BHist}$ be public $\StreamNameUp$
endpoints, and let $\mathcal P$ be a StreamName tail-window coverage packet
over a finite $\mathsf{ProbeBundle}$. Suppose the selected observations of
$\mathcal P$ split into displayed prefix and suffix subbundles with a shared
boundary row. Then the restrictions of $\mathcal P$ to the prefix and suffix
subbundles are StreamName tail-window coverage packets over the same public
endpoints and the same accepted $\RegSeqRat$ spine.

The common-refinement recomposition of these two restricted packets recovers
$\mathcal P$ on every selected observation. Every finite $\RealUp$ consumer
row of $\mathcal P$ factors through either the prefix packet, the suffix
packet, or the boundary-overlap rows. No completion object, quotient
representative, host-index equality, metric-completeness row, arithmetic or
order operation, or standard bridge row is read by the recomposed packet.
\end{theorem}
\begin{proof}
Unfold the StreamName tail-window coverage packet of
\autoref{def:streamname-tail-window-coverage-packet}. Restricting to the
displayed prefix subbundle keeps the public StreamName endpoints, the selected
$\mathsf{UnaryHistory}/\mathsf{InBundle}$ rows in the prefix window, the
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, the DyadicRatCore endpoint rows read there, and the inherited
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ provenance. The same restriction
argument gives the suffix packet.

Apply \autoref{thm:streamname-tail-window-cover-common-refinement} to the
prefix and suffix packets. The generated packet is finite, its restrictions
recover the two displayed subbundles, and the shared boundary row is carried as
one row in the common packet rather than as two independent sources.

Next apply \autoref{thm:streamname-tail-window-refinement-associativity}. It
identifies the regrouping of the prefix packet, the boundary overlap, and the
suffix packet with the original finite window, so every selected observation
of $\mathcal P$ is recovered by the recomposed packet.

Now apply \autoref{thm:streamname-tail-window-terminal-source-uniqueness} and
\autoref{thm:streamname-tail-window-regseqrat-coverage-lock}. The finite
consumer source surface is therefore the displayed
StreamName/$\RegSeqRat$/DyadicRatCore source surface of either restricted
packet, together with the shared boundary rows when the consumer reads across
the split. The RegSeqRat and DyadicRatCore rows read by the prefix, suffix,
and recomposed packet are the same rows of the original finite ledger.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary}. The
finite $\RealUp$ consumer has no row for completion, quotient, host-index
equality, metric-completeness, arithmetic or order, standard bridge, or hidden
selector data, so the prefix/suffix recomposition cannot introduce any such
object.
\end{proof}

\begin{theorem}[StreamName tail-window cover-chain source confluence]
\label{thm:streamname-tail-window-cover-chain-source-confluence}
Let
$$
\mathcal P_0,\mathcal P_1,\ldots,\mathcal P_n
$$
be a finite chain of StreamName tail-window coverage packets over the same
public $\StreamNameUp$ endpoints and the same accepted $\RegSeqRat$ spine.
Assume each adjacent pair $\mathcal P_i,\mathcal P_{i+1}$ carries certified
overlap rows for the displayed finite windows, and assume the chain is closed
under the common-refinement operation of
\autoref{thm:streamname-tail-window-cover-common-refinement}. Then every packet
in the chain induces the same consumer-facing source surface for finite
$\RealUp$ reads.

Concretely, the common surface consists exactly of the finite-window classifier
rows, the selected $\mathsf{ProbeBundle}/\mathsf{InBundle}/\mathsf{UnaryHistory}$
rows, the pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted
$\RegSeqRat$ spine, the DyadicRatCore endpoint rows, and the
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ provenance rows transported along
the chain. The confluence statement exports no completion object, quotient
representative, host-index equality, metric-completeness row, arithmetic or
order row, standard bridge row, or hidden selector.
\end{theorem}
\begin{proof}
Induct on the finite chain length. For the base chain, apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization} and
\autoref{thm:streamname-tail-window-realup-boundary}. A single terminal packet
therefore exposes only the finite StreamName/$\RegSeqRat$/DyadicRatCore source
surface and its displayed continuation ledger.

For the induction step, compare the already-confluent initial subchain with the
last packet. The certified overlap rows allow
\autoref{thm:streamname-tail-window-cover-common-refinement} to form the common
finite packet for the terminal member of the subchain and the last packet.

Use \autoref{thm:streamname-tail-window-refinement-associativity} to identify
this refinement with the refinement obtained by first recomposing the earlier
chain and then attaching the last overlap. Apply
\autoref{thm:streamname-tail-window-terminal-source-uniqueness} to the two
terminal packets inside that common refinement, and apply
\autoref{thm:streamname-tail-window-regseqrat-coverage-lock} to keep the
accepted rational-sequence spine and DyadicRatCore endpoint rows fixed.

Finally apply \autoref{thm:streamname-tail-window-realup-boundary} to the
exported finite consumer. The boundary theorem removes completion, quotient,
host-index equality, metric-completeness, arithmetic or order, standard bridge,
and hidden-selector data from the readout, so the confluence is a statement
only about the displayed finite source rows.
\end{proof}

\begin{theorem}[StreamName tail-window terminal coverage]
\label{thm:streamname-tail-window-terminal-coverage}
Any terminal $\RealUp$ read induced by a finite $\StreamNameUp$ tail-window
cover chain is covered by exactly the common finite source surface of
\autoref{thm:streamname-tail-window-cover-chain-source-confluence}. Thus the
terminal read exposes the finite-window classifier rows, selected
$\mathsf{ProbeBundle}/\mathsf{InBundle}/\mathsf{UnaryHistory}$ rows, pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine,
DyadicRatCore endpoint rows, and transported
$\Cont/\hsame/\Pkg/\mathsf{RealLedgerPolicy}$ provenance rows.

It exposes no completion object, quotient representative, host-index equality,
metric-completeness row, arithmetic or order row, standard bridge row, or hidden
selector.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-tail-window-cover-chain-source-confluence} to the
finite cover chain. The induced terminal source is the common finite surface
carried by every packet in the chain.

Next apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization}. It routes
the terminal RealUp read through the displayed StreamName, RegSeqRat, and
DyadicRatCore source rows rather than through an external completion carrier.

Finally use \autoref{thm:streamname-tail-window-realup-boundary}. The boundary
removes quotient representatives, host-index equality, metric-completeness
rows, arithmetic and order rows, standard bridge rows, and hidden selectors from
the terminal read. Therefore the read is covered exactly by the common finite
source surface from the confluence theorem.
\end{proof}
