\begin{theorem}[StreamName-RegSeqRat uniform finite-window seal]
\label{thm:streamname-regseqrat-uniform-finite-window-seal}
Let $W$ be a finite $\mathsf{BHist}$ observation window for a public
$\StreamNameUp$ rational stream package, and suppose that the two endpoints
of $W$ satisfy $\mathsf{RatStreamNameFiniteWindowClassifier}$. Then the
StreamName pointwise seal, the $\RegSeqRat$ scheduled seal, every certified
nested-window handoff through $W$, and the finite-window $\RealUp$ readback
select the same finite observation packet under $\hsame$.

The common packet consists exactly of the pointwise
$\mathsf{RatStreamNameCarrier}$ and
$\mathsf{RatStreamNameClassifier}$ observations at the certified unary
indices of $W$, the accepted $\RegSeqRat$ pointwise seal rows, the
$\RealUp$ endpoint seal row, the finite $\Cont$ ledger, the
$\mathsf{ProbeBundle}$ membership rows, and the shared $\Pkg$ provenance.
It contains no quotient representative, completion modulus, host index
equality, or additional regularity datum.
\end{theorem}
\leanchecked{BEDC.Derived.StreamNameUp.StreamnameRegseqratUniformFiniteWindowSeal}
\begin{proof}
First form the pointwise seal over the certified endpoints of $W$. Apply
\autoref{thm:streamname-regseqrat-pointwise-seal-stability} at each unary
index. The endpoint classifier hypotheses give the same carrier row,
classifier row, $\hsame$ transport, finite $\Cont$ route, $\Pkg$ provenance,
and accepted $\mathsf{DyadicRatCore}$ ledger entry for the StreamName and
$\RegSeqRat$ reads.

Next paste these pointwise rows over the whole finite window. By
\autoref{thm:streamname-regseqrat-pointwise-seal-pasting}, the scheduled
$\RegSeqRat$ seal over $W$ is the unique finite packet assembled from those
rows and the same finite ledger. No quotient or completion representative is
introduced by this pasting step.

Now compare all certified subwindows of $W$. Use
\autoref{thm:streamname-regseqrat-nested-window-handoff} to identify the
direct and nested handoff routes with the same restricted source surface.
Thus every nested-window consumer sees the pointwise packet just constructed,
with the same $\mathsf{ProbeBundle}$ membership rows and $\hsame$
comparisons.

Finally apply
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}. The triple cover
identifies the StreamName window package, the $\RegSeqRat$ scheduled seal,
and the $\RealUp$ endpoint readback whenever their unary observations,
finite $\Cont$ ledger, $\hsame$ transports, and $\Pkg$ provenance agree.
Combining the four steps gives one uniform finite-window seal packet under
$\hsame$.
\end{proof}

\begin{theorem}[StreamName RealUp finite-window seal boundary]
\label{thm:streamname-realup-seal-boundary}
Let $W$ be a finite public $\StreamNameUp$ rational observation window whose
endpoints satisfy $\mathsf{RatStreamNameFiniteWindowClassifier}$. Suppose that
the $\RegSeqRat$ handoff over $W$ carries accepted pointwise seal rows, the
finite $\Cont$ ledger, the $\mathsf{ProbeBundle}$ membership rows, the
corresponding $\mathsf{InBundle}$ rows, the $\mathsf{UnaryHistory}$
observations, and shared $\mathsf{Pkg}$ provenance. Then these rows determine
exactly the finite-window $\RealUp$ seal boundary read from $W$.

Conversely, every public finite-window $\RealUp$ seal read arising from this
handoff factors through those same StreamName source rows, accepted
$\RegSeqRat$ pointwise seal rows, bundle-membership rows, unary observations,
finite ledger entries, and provenance rows. The boundary contains no completion
object, quotient representative, host index equality, or regularity datum
outside the displayed $\RegSeqRat$ seal.
\end{theorem}
\begin{proof}
First recover the StreamName source surface. Apply
\autoref{thm:streamname-real-regseq-finite-window-handoff}. It identifies the
finite public window read with the displayed rational StreamName observations,
the unary histories at the certified indices, the finite $\Cont$ routes, and
the shared $\Pkg$ provenance.

Next pass to the scheduled rational seal. By
\autoref{thm:streamname-regseqrat-scheduled-seal-exhaustion}, the
$\RegSeqRat$ side contributes only the accepted pointwise seal rows over the
same unary observations, the same bundle-membership rows, and the same finite
ledger. No additional sequence regularity row is available at this step.

Now compare the three visible seal surfaces. Use
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover}. The StreamName
window, the $\RegSeqRat$ scheduled seal, and the $\RealUp$ endpoint readback
cover one another exactly when their unary observations, bundle rows, finite
transport ledger, $\hsame$ comparisons, and provenance agree.

Finally apply
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. Uniformity over
nested finite windows prevents a later subwindow from adding completion data,
quotient representatives, host index equality, or hidden regularity data.
Thus the forward direction gives a unique finite-window $\RealUp$ seal
boundary, and the reverse direction factors every public read through precisely
the displayed rows.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-RealUp seal pullback uniqueness]
\label{thm:streamname-regseqrat-realup-seal-pullback-uniqueness}
Let $W$ be a finite public $\StreamNameUp$ rational observation window. Suppose
two finite-window $\RealUp$ seal reads over $W$ arise from the same StreamName
window rows, the same accepted $\RegSeqRat$ pointwise seal rows, the same
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ membership rows, the same
$\mathsf{UnaryHistory}$ observations, the same finite $\Cont$ ledger, the same
$\hsame$ transports, and the same $\Pkg$ provenance. Then the two reads
determine the same $\RealUp$ finite-window seal boundary.

Conversely, any equality of $\RealUp$ finite-window seal boundaries arising
from $W$ factors back through that displayed StreamName--$\RegSeqRat$ source
surface: the common boundary is witnessed by the same StreamName window rows,
the same accepted pointwise seal rows, the same bundle-membership rows, the
same unary observations, the same finite ledger, the same $\hsame$ transport
surface, and the same provenance. This pullback uses no quotient stream,
selected host limit, host index equality, completion witness, or ambient
completeness assumption.
\end{theorem}
\begin{proof}
First expose the source surface for each read. Apply
\autoref{thm:streamname-real-regseq-finite-window-handoff} to both
finite-window handoffs. The common StreamName window rows, unary observations,
finite $\Cont$ routes, $\hsame$ transports, and $\Pkg$ provenance give the same
public source packet.

Next exhaust the rational scheduled seal. By
\autoref{thm:streamname-regseqrat-scheduled-seal-exhaustion}, each handoff has
only the displayed accepted $\RegSeqRat$ pointwise seal rows, the same
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ membership rows, and the same
finite ledger available to it.

The three seal surfaces now compare over a single packet. Use
\autoref{thm:streamname-regseqrat-realup-triple-seal-cover} to identify the
StreamName window surface, the $\RegSeqRat$ scheduled seal, and the $\RealUp$
readback surface. Then
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal} prevents any
nested finite subwindow from changing that packet.

It remains to read off the boundary. Apply
\autoref{thm:streamname-realup-seal-boundary}. The forward direction gives
equality of the two $\RealUp$ finite-window seal boundaries. The converse
direction says that any such equality is already a factorization through the
same StreamName--$\RegSeqRat$ source rows, so no quotient stream, selected host
limit, host index equality, completion witness, or ambient completeness datum
can enter the pullback.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-RealUp terminal pullback factorization]
\label{thm:streamname-regseqrat-realup-terminal-pullback-factorization}
Let $W$ be a finite public $\StreamNameUp$ rational observation window, and
let $R$ be a terminal finite-window $\RealUp$ seal read over $W$. Suppose $R$
is presented through the public StreamName rational window interface and the
accepted $\RegSeqRat$ pointwise seal over that window. Then $R$ factors
through exactly the StreamName point rows, the $\RegSeqRat$ pointwise seal
rows, the $\RealUp$ finite-window seal boundary, the finite $\Cont$ ledger,
the $\hsame$ transports, the $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ membership rows, the $\mathsf{UnaryHistory}$
observations, and the shared $\Pkg$ provenance.

Conversely, the displayed StreamName point rows, accepted $\RegSeqRat$
pointwise seal rows, $\RealUp$ boundary row, finite $\Cont$ ledger,
$\hsame$ transports, bundle-membership rows, unary observations, and
provenance rows repack into the same terminal finite-window $\RealUp$ seal
boundary. The factorization carries no quotient stream, selected host limit,
host index equality, completion witness, ambient completeness row, or
metric-completeness row.
\end{theorem}
\begin{proof}
First build the uniform public packet. Apply
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. It identifies
the StreamName point rows and accepted $\RegSeqRat$ pointwise seal rows over
$W$ with one finite observation packet under the same $\hsame$ transports,
finite $\Cont$ ledger, bundle-membership rows, unary observations, and
provenance.

Next read the terminal boundary of the $\RealUp$ seal. Use
\autoref{thm:streamname-realup-seal-boundary}. The forward direction says that
the displayed public packet determines the finite-window $\RealUp$ seal
boundary, and the reverse direction repacks those same rows into the boundary
read.

Finally compare any two terminal presentations of the read. Apply
\autoref{thm:streamname-regseqrat-realup-seal-pullback-uniqueness}. The
pullback uniqueness identifies presentations with the same StreamName rows,
accepted $\RegSeqRat$ rows, bundle-membership rows, unary observations,
$\Cont$ ledger, $\hsame$ transports, and provenance.

The preceding steps give both directions of the factorization. Since each
ingredient is read from the displayed finite packet and its $\RealUp$ boundary,
there is no row from quotient streams, selected host limits, host index
equality, completion witnesses, ambient completeness, or metric-completeness
data available to the terminal seal.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-DyadicRatCore-RealUp terminal pullback factorization]
\label{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}
Let $W$ be a finite public $\StreamNameUp$ rational observation window, and
let $R$ be a terminal finite-window $\RealUp$ seal read over $W$. Suppose $R$
is presented through the public StreamName rational window interface, the
accepted $\RegSeqRat$ pointwise seal over that window, and the
$\DyadicRatCoreUp$ endpoint-radius-distance ledger anchored to the same
window. Then $R$ factors through exactly four visible faces: the StreamName
point and window rows, the $\DyadicRatCoreUp$ endpoint-radius-distance ledger,
the $\RegSeqRat$ pointwise and readback rows, and the local $\RealUp$
finite-window seal boundary.

The only support rows available to this factorization are the displayed
$\BHist$ observations, componentwise $\hsame$ transports, finite $\Cont$
routes, shared $\Pkg$ provenance, $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ membership rows, $\mathsf{UnaryHistory}$ observations, and
local $\NameCert$ support. Conversely, any packet displaying precisely those
four faces and support rows repacks into the same terminal finite-window
$\RealUp$ seal read. It exports no quotient stream equality, selected host
limit, host real equality, ambient completeness row, metric-completeness row,
bridge row, trichotomy row, open-cover compactness row, or choice datum.
\end{theorem}
\begin{proof}
Start from the three-face terminal pullback of
\autoref{thm:streamname-regseqrat-realup-terminal-pullback-factorization}. It
places the terminal $\RealUp$ finite-window read on the StreamName point rows,
accepted $\RegSeqRat$ pointwise seal rows, and $\RealUp$ seal boundary, with
the displayed finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$
support.

Next insert the dyadic ledger face. Apply
\autoref{thm:streamname-regseqrat-dyadic-real-four-face-exactness}. Its
forward direction says that an accepted seal-facing read has exactly the
StreamName, $\RegSeqRat$, $\DyadicRatCoreUp$, and $\RealUp$ faces, with the
listed finite support rows. Its converse direction repacks any packet with
those four faces into the same admissible public interface.

It remains to identify the dyadic face with the same finite window used by the
regular-rational readback. Use the Dyadic-RegSeq route factorization
\autoref{thm:streamname-dyadic-regseq-route-factorization}, as cited in the
four-face exactness proof. This pins every endpoint, radius, distance, and
readback coordinate to $W$ before either the $\RegSeqRat$ or $\RealUp$
consumer can inspect the packet.

Combining these steps gives both directions of the terminal pullback. The
three-face theorem supplies the StreamName--$\RegSeqRat$--$\RealUp$ terminal
boundary, the four-face exactness theorem supplies the
$\DyadicRatCoreUp$ ledger as the fourth visible face, and the route
factorization prevents a detached tolerance route from entering the packet.

The excluded objects are therefore not public coordinates of the factorization.
There is no quotient stream equality, selected host limit, host real equality,
ambient completeness row, metric-completeness row, bridge row, trichotomy row,
open-cover compactness row, or choice datum available to the terminal read.
\end{proof}

\begin{theorem}[StreamName-RegSeqRat-RealUp composite terminal pullback]
\label{thm:streamname-regseqrat-realup-composite-terminal-pullback}
Let $W$ be a finite public $\StreamNameUp$ rational observation window. Suppose
two consecutive terminal pullback readings pass first through the displayed
$\mathsf{RatStreamNameCarrier}$ and $\mathsf{RatStreamNameClassifier}$ rows of
$W$, then through the accepted $\RegSeqRat$ pointwise seal rows, and finally to
the $\RealUp$ finite-window seal boundary. Then the two-stage terminal reading
determines exactly the same finite $\BHist$ packet as the single composite
pullback from the StreamName rows into the $\RealUp$ boundary row.

The shared packet consists precisely of the
$\mathsf{RatStreamNameCarrier}$ rows, the
$\mathsf{RatStreamNameClassifier}$ rows, the accepted $\RegSeqRat$ pointwise
seal rows, the $\RealUp$ boundary row, the $\mathsf{ProbeBundle}$ rows, the
$\mathsf{InBundle}$ membership rows, the $\mathsf{UnaryHistory}$ observations,
the finite $\Cont$ ledger, the componentwise $\hsame$ transports, the common
$\Pkg$ provenance, and the local $\NameCert$ witnessing the public StreamName
window. It contains no quotient stream, selected host limit, host index
equality, completion witness, ambient completeness row, or metric-completeness
row.
\end{theorem}
\begin{proof}
First build the finite public packet over $W$. Apply
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. This identifies
the displayed StreamName carrier and classifier rows with the accepted
$\RegSeqRat$ pointwise seal rows, the bundle rows, the unary observations, the
finite $\Cont$ ledger, the componentwise $\hsame$ transports, and the shared
$\Pkg$ provenance.

Next read the endpoint seal as a boundary row. Use
\autoref{thm:streamname-realup-seal-boundary}. The boundary construction says
that the same packet determines the $\RealUp$ finite-window seal boundary, and
that every public boundary read factors back through the same StreamName rows,
accepted $\RegSeqRat$ rows, $\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$
rows, $\mathsf{UnaryHistory}$ observations, finite ledger, transports, and
provenance.

Now compare the two consecutive pullback readings with the direct composite
reading. Apply
\autoref{thm:streamname-regseqrat-realup-seal-pullback-uniqueness}. Since both
routes expose the same finite source surface and the same $\RealUp$ boundary
row, pullback uniqueness identifies their finite $\BHist$ packets component by
component.

Finally invoke
\autoref{thm:streamname-regseqrat-realup-terminal-pullback-factorization}. The
terminal factorization repacks the identified packet through the local
$\NameCert$ and shows that neither the two-stage route nor the composite route
has access to a quotient stream, selected host limit, host index equality,
completion witness, ambient completeness row, or metric-completeness row. Thus
the consecutive and composite terminal pullbacks are the same finite public
packet.
\end{proof}

\begin{theorem}[StreamName terminal reindex pullback invariance]
\label{thm:streamname-terminal-reindex-pullback-invariance}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation
packet, and let $R$ be a certified public finite-window reindex route for
$W$. Suppose $R$ preserves the public finite observation section, the certified
endpoint rows, the displayed $\BHist$, the componentwise $\hsame$ transports,
the finite $\Cont$ ledger, the shared $\Pkg$ provenance, and the local
$\NameCert$ rows. Then the terminal pullback read through
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ is
invariant under $R$.

The invariant packet has the same visible StreamName window, the same
$\DyadicRatCoreUp$ endpoint-radius-distance ledger, the same $\RegSeqRatUp$
accepted readback rows, the same $\RealUp$ boundary row, and the same support
rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
It introduces no quotient stream equality, selected host limit, host real
equality, ambient completeness row, metric-completeness row, bridge row,
trichotomy row, open-cover compactness row, or choice datum.
\end{theorem}
\begin{proof}
First read the reindexed StreamName side. Apply
\autoref{thm:streamname-terminal-reindex-four-face-pullback}. Its hypotheses
are exactly the preserved public finite observation section, endpoint rows,
displayed $\BHist$, componentwise $\hsame$, finite $\Cont$ ledger, shared
$\Pkg$, and local $\NameCert$ rows, so the reindexed route reaches the same
terminal four-face pullback surface.

Next pin the four visible faces of that surface. Apply
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
The factorization says that the terminal read has only the displayed
$\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ readback,
$\RealUp$ boundary row, and the listed support rows. Since the reindex route
preserves those rows component by component, the visible faces are unchanged.

Finally compare the two-stage and direct terminal reads. By
\autoref{thm:streamname-regseqrat-realup-composite-terminal-pullback}, both
presentations determine one finite $\BHist$ packet over the same support
surface. Hence the terminal pullback is invariant under $R$, and no quotient,
selected host limit, host real equality, completeness, bridge, trichotomy,
open-cover compactness, or choice coordinate is added.
\end{proof}

\begin{theorem}[StreamName terminal pullback idempotence]
\label{thm:streamname-terminal-pullback-idempotence}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation
packet. Suppose a terminal four-face pullback packet over $W$ already exposes
exactly the StreamName finite window, the $\DyadicRatCoreUp$
endpoint-radius-distance ledger, the $\RegSeqRatUp$ accepted readback rows,
the $\RealUp$ finite-window seal boundary, and the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Suppose further that the same packet displays the corresponding
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and
$\mathsf{UnaryHistory}$ rows required by the public finite observation
surface. Then applying the terminal pullback reading to this packet again
exposes the same finite BEDC packet.

Equivalently, the terminal four-face pullback is a normal form for certified
public StreamName finite-window reads: after the four visible faces and their
support rows are present, a further terminal reading cannot add a quotient
stream, host equality, selected limit, ambient completeness row,
metric-completeness row, bridge row, trichotomy row, open-cover compactness
row, or choice coordinate.
\end{theorem}
\begin{proof}
First identify the packet already in hand. Apply
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
Its converse direction repacks exactly the displayed StreamName,
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces, together with the
listed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, bundle, unary-history, and
$\NameCert$ support rows, into the terminal finite-window seal read over $W$.

Next compare the second reading with the first one. By
\autoref{thm:streamname-regseqrat-realup-composite-terminal-pullback}, a
two-stage terminal read and the direct composite read determine the same
finite $\BHist$ packet whenever they expose the same StreamName rows,
accepted $\RegSeqRatUp$ rows, $\RealUp$ boundary row, finite ledger,
transports, provenance, bundle rows, unary observations, and local
$\NameCert$ support.

Finally account for certified reindex routes. Apply
\autoref{thm:streamname-terminal-reindex-pullback-invariance}. Any certified
route preserving the displayed finite observation section, endpoint rows,
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows reaches the same
terminal four-face surface. Thus the second terminal read has no coordinate
outside the normal-form packet, and the excluded quotient, host-equality,
selected-limit, completeness, bridge, trichotomy, open-cover compactness, and
choice data remain unavailable.
\end{proof}

\begin{theorem}[StreamName terminal four-face support deletion obstruction]
\label{thm:streamname-terminal-four-face-support-deletion-obstruction}
Let $W$ be a certified public $\StreamNameUp$ finite-window packet whose terminal
four-face read exposes exactly the $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and local $\RealUp$ faces. Suppose the displayed support surface
consists of
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert
$$
together with the public finite-observation rows $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$. If any one of the displayed
support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or $\NameCert$ is deleted, or
if one of the public finite-observation rows $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$, or $\mathsf{UnaryHistory}$ is deleted, the remaining packet
is not accepted as a terminal four-face pullback over $W$.

The missing row cannot be supplied by quotient stream equality, selected host
limits, host equality, countable choice, ambient completeness,
metric-completeness, bridge rows, trichotomy, or open-cover compactness.
\end{theorem}
\begin{proof}
First identify the four visible faces and their support surface. Apply
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
It says that an accepted terminal read over $W$ factors through exactly the
StreamName window, dyadic endpoint-radius-distance ledger, $\RegSeqRatUp$
readback rows, and local $\RealUp$ finite-window boundary, with only the
displayed BEDC support rows and public finite-observation rows available.

Next remove one displayed row. For one of $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
or $\NameCert$, apply
\autoref{thm:streamname-open-phase-finite-window-support-row-minimality}. That
minimality result says that deleting any of these rows destroys the public
finite-window support needed by the StreamName packet before the terminal
pullback can be formed.

For one of $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, or
$\mathsf{UnaryHistory}$, use the same four-face factorization. These rows are
part of the public finite-observation surface read by the factorization itself,
so deleting one removes a coordinate required by the accepted terminal packet.

Finally compare with the normal form. By
\autoref{thm:streamname-terminal-pullback-idempotence}, a complete support
surface is stable under another terminal read. Hence the converse direction of
the four-face factorization can repack only the complete surface, not the
shortened packet. The excluded quotient, host-limit, host-equality, choice,
completeness, bridge, trichotomy, and compactness rows are not coordinates of
that normal form, so none of them can fill the missing support row.
\end{proof}

\begin{theorem}[StreamName terminal pullback support exactness]
\label{thm:streamname-terminal-pullback-support-exactness}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation
packet. A terminal four-face pullback packet over $W$ is accepted exactly when
it exposes the StreamName finite window, the $\DyadicRatCoreUp$
endpoint-radius-distance ledger, the $\RegSeqRatUp$ accepted readback rows,
the local $\RealUp$ finite-window seal boundary, and exactly the displayed
support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert,
$$
together with the public finite-observation rows
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and
$\mathsf{UnaryHistory}$.

Conversely, any packet over $W$ with exactly those visible faces and support
rows repacks into the same terminal four-face pullback normal form. The
acceptance test exports no quotient stream, selected host limit, host
equality, countable choice, ambient completeness row, metric-completeness row,
bridge row, trichotomy row, or open-cover compactness row.
\end{theorem}
\begin{proof}
For the forward direction, start from the terminal four-face factorization of
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
It identifies every accepted terminal read over $W$ with the StreamName
finite-window face, the dyadic endpoint-radius-distance ledger, the
$\RegSeqRatUp$ readback face, the $\RealUp$ finite-window boundary, and the
listed finite support rows.

Next use
\autoref{thm:streamname-terminal-reindex-pullback-invariance}. Since certified
reindex routes preserve the public finite observation section, endpoint rows,
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, support cannot be
enlarged by changing the terminal presentation of the same window.

The local deletion obstruction is
\autoref{thm:streamname-terminal-four-face-support-deletion-obstruction}. It
says that deleting any displayed BEDC support row, or any public
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, or $\mathsf{UnaryHistory}$
observation row, prevents acceptance, and that quotient, host-limit,
host-equality, choice, completeness, bridge, trichotomy, and compactness rows
cannot replace the missing coordinate.

For the reverse direction, assume a packet displays exactly those four faces
and support rows. The converse direction of
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}
repacks it into the terminal finite-window seal read over $W$.

Finally apply
\autoref{thm:streamname-terminal-pullback-idempotence}. Once the four faces,
the five BEDC support rows, and the three public finite-observation rows are
present, another terminal read returns the same packet. Hence the support list
is both sufficient and necessary for acceptance, and quotient streams,
selected host limits, host equality, countable choice, ambient completeness,
metric-completeness rows, bridges, trichotomy, and open-cover compactness
remain outside the normal form.
\end{proof}

\begin{theorem}[StreamName terminal pullback support induction]
\label{thm:streamname-terminal-pullback-support-induction}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation packet.
For the terminal four-face pullback over $W$, order the support rows as
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert,\quad
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory}.
$$
An accepted terminal four-face pullback over $W$ is obtained by finite
induction over this ordered support list: the empty prefix carries no accepted
terminal extension, and each proper prefix has an accepted extension to the
next prefix exactly when the next displayed row in the list is present. The
full prefix is the unique terminal normal form over the $\StreamNameUp$,
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and local $\RealUp$ faces.

No quotient stream, selected host limit, host equality, countable choice,
ambient completeness row, metric-completeness row, bridge row, trichotomy row,
or open-cover compactness row can replace a missing step of this finite
support induction.
\end{theorem}
\begin{proof}
The base stage is the deletion obstruction. By
\autoref{thm:streamname-terminal-four-face-support-deletion-obstruction},
removing any one of the displayed BEDC support rows or public
finite-observation rows prevents acceptance. In particular the empty prefix,
and every prefix missing its next displayed row, cannot be accepted as the
terminal four-face pullback over $W$.

For the induction step, assume a prefix of the displayed list has been built
and consider the next row. If that next row is absent, the deletion obstruction
again blocks acceptance, and the refused replacement rows cannot fill the
coordinate. If the next row is present, the prefix extends by the corresponding
finite BEDC support coordinate or public finite-observation coordinate.

At the terminal stage, apply
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
It repacks exactly the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$,
and local $\RealUp$ faces together with the complete displayed support list.
Then use \autoref{thm:streamname-terminal-pullback-support-exactness} to
identify that complete list as necessary and sufficient for acceptance.

Finally apply \autoref{thm:streamname-terminal-pullback-idempotence}. Once the
full support prefix is present, a further terminal read returns the same
packet, so no second terminal normal form exists over the four faces. The
explicit refusals of quotient streams, selected host limits, host equality,
countable choice, ambient completeness, metric-completeness rows, bridge rows,
trichotomy, and open-cover compactness remain part of the induction invariant
at every prefix.
\end{proof}

\begin{theorem}[StreamName terminal pullback row-order determinacy]
\label{thm:streamname-terminal-pullback-row-order-determinacy}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation packet.
Suppose an accepted terminal four-face pullback over $W$ has support built by
the induction of
\autoref{thm:streamname-terminal-pullback-support-induction}. Then the support
row order is uniquely fixed as
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert,\quad
\mathsf{ProbeBundle},\quad \mathsf{InBundle},\quad
\mathsf{UnaryHistory}.
$$
Swapping two displayed rows, omitting a displayed row, or replacing a
displayed row by any other row fails to present the same terminal normal form
over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and local $\RealUp$.

In particular, quotient streams, selected host limits, host equality,
countable choice, ambient completeness rows, metric-completeness rows, bridge
rows, trichotomy rows, and open-cover compactness rows are not replacement
rows for this terminal support order.
\end{theorem}
\begin{proof}
Start with
\autoref{thm:streamname-terminal-pullback-support-induction}. It builds the
accepted terminal support by the displayed finite prefix order, so each stage
has a distinguished next row and the full prefix is the terminal normal form
over the four faces.

The exactness theorem,
\autoref{thm:streamname-terminal-pullback-support-exactness}, identifies the
same displayed list as the necessary and sufficient support for acceptance.
Thus omitting any row leaves the exact support surface, and inserting a row
outside the list does not repair the missing BEDC or public
finite-observation coordinate.

Next apply
\autoref{thm:streamname-terminal-four-face-support-deletion-obstruction}. It
rules out acceptance after deleting any displayed row and also rules out
quotient streams, selected host limits, host equality, countable choice,
ambient completeness, metric-completeness rows, bridge rows, trichotomy, and
open-cover compactness as substitutes for a missing coordinate.

Now use
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}.
The four-face factorization repacks exactly the $\StreamNameUp$ window, the
$\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ readback face, the local
$\RealUp$ boundary, and the displayed support rows. A swapped presentation
therefore fails to match the prefix route used to construct that factorized
packet.

Finally apply \autoref{thm:streamname-terminal-pullback-idempotence}. Once the
ordered support list has reached the terminal packet, a further terminal read
returns the same packet. Hence the accepted row order is deterministic, and no
swapped, omitted, or replaced support list presents the same terminal normal
form.
\end{proof}

\begin{theorem}[StreamName terminal pullback metric-completion refusal]
\label{thm:streamname-terminal-pullback-metric-completion-refusal}
Let $W$ be a certified public $\StreamNameUp$ finite-window observation packet,
and suppose its terminal four-face pullback is accepted. No consumer can
reinterpret that accepted packet as a $\MetricSpaceUp$ row, a
$\CompleteMetricUp$ row, or an ambient-completeness witness unless the
metric or completion row is separately displayed outside the terminal pullback
surface.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-regseqrat-dyadic-realup-terminal-pullback-factorization}
to identify the accepted terminal surface. It exposes the StreamName finite
window, the $\DyadicRatCoreUp$ endpoint-radius-distance ledger, the
$\RegSeqRatUp$ readback rows, and the local $\RealUp$ finite-window boundary.

Now read the support list through
\autoref{thm:streamname-terminal-pullback-support-exactness}. The only support
coordinates exported with those four faces are $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, $\NameCert$, $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and
$\mathsf{UnaryHistory}$. A $\MetricSpaceUp$ row, a $\CompleteMetricUp$ row, and
an ambient-completeness witness are not entries of that exact list.

It remains to rule out hidden replacement by an omitted coordinate. Use
\autoref{thm:streamname-terminal-four-face-support-deletion-obstruction}: a row
missing from the terminal support cannot be supplied by a quotient stream,
selected host limit, host equality, countable choice, ambient completeness,
metric-completeness row, bridge row, trichotomy, or compactness row.

Therefore any consumer that wants metric structure or completion data must
display that data as a separate row outside the terminal pullback surface. The
accepted StreamName--DyadicRatCore--RegSeqRat--Real four-face packet itself
does not certify a metric space, a complete metric space, or ambient real
completeness.
\end{proof}
