\begin{theorem}[StreamName terminal four-face support minimality]
\label{thm:streamname-terminal-four-face-support-minimality}
Let $U$ be an accepted current Phase Real and Completion terminal
$\StreamNameUp$ request section. Then the public terminal surface of $U$ is
accepted exactly through the four visible faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ together with the
displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$ support rows.

Moreover, this support is minimal for the accepted public verdict: deleting any
one of the four faces, or deleting any one of the displayed support rows,
prevents the resulting packet from presenting the same carrier verdict and the
same classifier verdict to Real-facing or completion-facing consumers. The
minimality claim uses no quotient stream equality, host sequence equality,
selected limits, countable choice, ambient $\RealUp$ completeness,
metric-completeness data, aggregate formalstatus row, or bridge row.
\end{theorem}
\begin{proof}
First build the public classifier surface. Apply
\autoref{thm:streamname-finite-section-cover-descent-classifier-reflection} to
the accepted terminal request section and its finite cover, then compare any
two public presentations with
\autoref{thm:streamname-finite-cover-common-refinement-classifier-uniqueness}.
These results place the carrier and classifier verdicts on the same visible
StreamName, DyadicRatCore, RegSeqRat, and Real faces over the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next lock the StreamName side to the dyadic, regular-rational, and Real sides.
The theorem
\autoref{thm:streamname-finite-section-real-regseq-dyadic-lock} says that a
Real-facing or completion-facing read of the terminal request section can use
only the finite StreamName window, the DyadicRatCore ledger, the RegSeqRat
readback, the Real seal boundary, and the same support rows. Thus a packet
with one visible face or one support row removed is no longer the packet seen
by those consumers.

Now read the same packet from the RegSeqRat terminal boundary. By
\autoref{thm:regseqrat-real-terminal-four-face-exactness}, terminal acceptance
is equivalent to the presence of exactly the four displayed faces with the
shared support rows. By
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness}, any accepted
consumer with the same public verdict has the same finite RegSeqRat source.
Hence removing a face or support row removes the witness needed to identify the
source that presents that verdict.

Finally pass through the Real dependency lattice. The exit totality theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every current
Phase Real and Completion terminal read through the ordered four-face route and
the displayed support rows. Combining this totality with the classifier
reflection and source-uniqueness steps gives the stated minimality: the public
carrier and classifier verdicts survive exactly on the four-face support
surface and not on any shorter packet.

The exclusion list follows from the same route description. None of the cited
surfaces contains a coordinate for quotient stream equality, host sequence
equality, selected limits, countable choice, ambient $\RealUp$ completeness,
metric-completeness data, aggregate formalstatus, or bridge rows, so those
objects cannot replace a missing visible face or support row.
\end{proof}

\begin{theorem}[StreamName terminal support defect localization]
\label{thm:streamname-terminal-support-defect-localization}
Let $U$ be an accepted current Phase Real and Completion terminal
$\StreamNameUp$ request section. Suppose a public terminal presentation of
$U$ fails to preserve at least one of the carrier verdict, the classifier
verdict, or the consumer-facing terminal route supplied by
\autoref{thm:streamname-terminal-four-face-support-minimality}. Then the
failure is witnessed on one of the four visible faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, or on one of the
displayed support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$.

Consequently, quotient stream equality, host sequence equality, selected
limits, countable choice, ambient $\RealUp$ completeness, metric completeness,
aggregate formalstatus, and bridge rows cannot be the carrier of such a
defect.
\end{theorem}
\begin{proof}
The minimality theorem
\autoref{thm:streamname-terminal-four-face-support-minimality} identifies the
only support surface that presents the accepted carrier verdict and classifier
verdict to Real-facing and completion-facing consumers. Therefore any loss of
one of those verdicts, or of the displayed terminal route, must remove
something from that support surface.

The readback theorem
\autoref{thm:streamname-open-phase-four-face-exit-readback} sends the public
exit of an accepted terminal request through the same StreamName,
DyadicRatCore, RegSeqRat, and Real faces. The Real-side localization theorem
\autoref{thm:real-l10-face-axis-defect-localization} says that an L10 exit
failure is detected on a displayed face or support row rather than on a hidden
quotient, limit, choice, completeness, aggregate-status, or bridge coordinate.

Combining these two route descriptions with the two-axis roadmap discipline
gives the advertised referee check. The theory axis records which face or
support row carries the terminal evidence, while the verification axis records
whether that row has been checked; neither axis turns the excluded quotient,
limit, completeness, choice, aggregate formalstatus, or bridge rows into
support for the StreamName terminal verdict.
\end{proof}

\begin{theorem}[StreamName terminal support defect pullback]
\label{thm:streamname-terminal-support-defect-pullback}
Let $U$ and $V$ be accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request sections. Suppose a consumer-visible terminal
presentation detects a carrier defect, a classifier defect, or a terminal
route defect on one of the visible faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, or on one displayed
support row $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, or local
$\NameCert$. Then the defect pulls back to a finite request-section mismatch:
it is witnessed by the finite-section pullback, by the Real-seal lock, by
window reindex determinacy, or by the terminal-window fusion source and
reindexing compatibility surfaces.

Consequently excluded coordinates such as quotient stream equality, host
sequence equality, selected limits, countable choice, metric completeness,
aggregate formalstatus, bridge rows, and ambient $\RealUp$ completeness cannot
serve as a defect carrier and cannot serve as a repair coordinate for the
terminal request section consumed by the L10 Real route.
\end{theorem}
\begin{proof}
First localize the visible failure. Apply
\autoref{thm:streamname-terminal-support-defect-localization}. The carrier,
classifier, or route defect is already forced onto one of the four visible
faces or onto one displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or
$\NameCert$ support row.

Now pass from the terminal presentation to the finite request section. Apply
\autoref{thm:streamname-finite-request-section-pullback}. The visible
StreamName terminal read is pulled back to the finite window and request rows
that the Phase $\RealUp$ route actually consumes. If the detected defect lies
on the Real boundary of that read, apply
\autoref{thm:streamname-finite-request-section-real-seal-lock}; the Real seal
identifies the same finite request section rather than a separate ambient
completion coordinate.

It remains to account for presentations that differ by window transport.
Apply \autoref{thm:streamname-window-reindex-determinacy}. The certified
reindexing data preserve the finite observation section, so a defect surviving
consumer-visible reindexing is still a mismatch of the same finite request
rows.

Finally use the fused terminal-window surface. The source-exhaustion theorem
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion} shows that
an accepted terminal-window packet has no source beyond the displayed
four-face section and support rows. The reindexing compatibility theorem
\autoref{thm:streamname-terminal-window-fusion-reindexing-compatibility}
keeps that source fixed under the allowed window transport. Thus every
visible support defect pulls back to the finite request-section evidence
listed in the statement.

The exclusion clause follows because none of the pullback, seal-lock,
determinacy, source-exhaustion, or compatibility surfaces exports a coordinate
for quotient stream equality, host sequence equality, selected limits,
countable choice, metric completeness, aggregate formalstatus, bridge rows, or
ambient $\RealUp$ completeness. Such data therefore cannot carry the detected
defect and cannot repair the finite section consumed by the L10 Real route.
\end{proof}

\begin{theorem}[StreamName terminal support removal witness]
\label{thm:streamname-terminal-support-removal-witness}
Let $U$ be an accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request section. Delete from the public terminal support of
$U$ either one visible face among
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, or one displayed support
row among $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$. Then the shortened request section cannot present the same
carrier verdict, classifier verdict, and consumer-facing terminal route as
$U$.

The lost verdict is witnessed as a finite request-section mismatch. If the
removed coordinate is the finite $\StreamNameUp$ window or one of its displayed
request rows, the witness is the finite-section pullback. If the removed
coordinate is the $\RealUp$ terminal boundary, the witness is the Real-seal
lock. If the removed coordinate is a transported window row, the witness is
window reindex determinacy. If the removed coordinate is part of the fused
terminal-window source, the witness is the terminal-window fusion surface.

No quotient stream equality, host sequence equality, selected limit, countable
choice, ambient $\RealUp$ completeness, metric completeness, aggregate
formalstatus row, or bridge row can repair the shortened section or replace the
finite witness.
\end{theorem}
\begin{proof}
Begin with the deletion. By
\autoref{thm:streamname-terminal-four-face-support-minimality}, every visible
face and every displayed support row named in the statement is a required
coordinate of the accepted terminal packet. Removing one of them therefore
loses the public carrier verdict, the public classifier verdict, or the
consumer-facing route.

Next localize the loss. Apply
\autoref{thm:streamname-terminal-support-defect-localization}. The failure
cannot be carried by an off-route equality, a selected limit, a choice row, a
completeness row, an aggregate verification row, or a bridge row. It is located
on the deleted face or support row itself.

Now pull the localized failure back to finite BEDC data. Use
\autoref{thm:streamname-terminal-support-defect-pullback}. A missing
StreamName window or displayed request row is read by the finite-section
pullback. A missing Real terminal boundary is read by the Real-seal lock. A
missing transported window row is read by window reindex determinacy. A missing
coordinate from the fused terminal source is read by the terminal-window fusion
source and reindexing compatibility surfaces.

These four witness surfaces exhaust the repair options available to the
terminal request section. Since none of them exports quotient stream equality,
host sequence equality, selected limits, countable choice, ambient Real
completeness, metric completeness, aggregate formalstatus rows, or bridge rows,
the shortened section has a finite request-section mismatch and no excluded
coordinate can repair it.
\end{proof}

\begin{theorem}[StreamName terminal four-face support exhaustion]
\label{thm:streamname-terminal-four-face-support-exhaustion}
Let $U$ be an accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request section. A consumer-visible support coordinate of $U$
is accepted if and only if it is one of the four terminal faces
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, or one of
the displayed rows $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$.

Consequently the accepted support of $U$ has no coordinate for quotient stream
equality, host sequence equality, selected limits, countable choice, ambient
$\RealUp$ completeness, metric-completeness data, aggregate formalstatus rows,
or bridge rows. None of these excluded data can be accepted as a substitute
support coordinate for the terminal request section.
\end{theorem}
\begin{proof}
For the reverse direction, the displayed four faces and support rows are
accepted by the terminal packet described in
\autoref{thm:streamname-terminal-four-face-support-minimality}. That theorem
already identifies the visible StreamName, DyadicRatCore, RegSeqRat, and Real
faces together with the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$ rows as the public terminal surface of $U$.

For the forward direction, let a consumer-visible support coordinate be
accepted by the current Phase Real and Completion terminal request section.
Apply \autoref{thm:streamname-finite-section-real-regseq-dyadic-lock}. The
consumer read is locked to the finite StreamName window, the DyadicRatCore
ledger, the RegSeqRat readback, the Real seal boundary, and the same displayed
support rows.

Next read the coordinate through the RegSeqRat terminal boundary. By
\autoref{thm:regseqrat-real-terminal-four-face-exactness}, terminal acceptance
is exactly the four-face packet with those displayed rows. By
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness}, an accepted
consumer with the same public verdict has the same finite RegSeqRat source, so
no second RegSeqRat-facing support source is available.

Finally pass to the Real exit route. Theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every current
Phase Real and Completion terminal read through the ordered
$\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$--$\RealUp$ route and the
displayed support rows. Therefore every accepted consumer-visible support
coordinate is one of exactly those faces or rows.

The excluded objects are not coordinates of that route. Quotient stream
equality, host sequence equality, selected limits, countable choice, ambient
$\RealUp$ completeness, metric-completeness data, aggregate formalstatus rows,
and bridge rows occur in neither the StreamName lock, the RegSeqRat exactness
and uniqueness surface, nor the Real exit-totality route. Hence none of them is
an accepted support coordinate for $U$.
\end{proof}

\begin{theorem}[StreamName terminal four-face support transport stability]
\label{thm:streamname-terminal-four-face-support-transport-stability}
Let $U$ and $V$ be accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request sections. Suppose their consumer-visible terminal
reads expose the same four visible faces
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, and suppose
their displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$ support rows agree after componentwise transport and replay. Then
$U$ and $V$ present the same consumer-visible terminal support packet.

The transport cannot introduce quotient stream equality, host sequence
equality, a selected limit, countable choice, metric-completeness data, an
aggregate formalstatus row, a bridge row, or an ambient $\RealUp$ completeness
row. The transported packet remains exactly the same four-face BEDC support
surface seen by Real-facing and completion-facing consumers.
\end{theorem}
\begin{proof}
First classify the accepted coordinates. Apply
\autoref{thm:streamname-terminal-four-face-support-exhaustion} to both
terminal request sections. Every consumer-visible support coordinate of either
section is therefore one of the four displayed faces or one of the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Next use the minimal support theorem. By
\autoref{thm:streamname-terminal-four-face-support-minimality}, no visible
face and no displayed support row can be deleted or substituted while
preserving the same Real-facing and completion-facing carrier and classifier
verdicts. Since the hypotheses identify the four faces and replay the support
rows componentwise, the two sections have the same StreamName-side public
surface.

Now pass through the RegSeqRat terminal route. The exactness theorem
\autoref{thm:regseqrat-real-terminal-four-face-exactness} reads the common
displayed faces as one terminal RegSeqRat four-face packet, and
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness} rules out a
second RegSeqRat source section with the same public verdict. Thus the
transported RegSeqRat component is the same finite source record.

Finally read the common packet through the Real L10 exit lattice. The theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every accepted
current Phase Real and Completion terminal read through the ordered
$\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$--$\RealUp$ route with the
displayed support rows. The two transported presentations therefore determine
the same terminal support packet, and the exhaustion theorem excludes every
off-route coordinate listed in the statement.
\end{proof}

\begin{theorem}[StreamName terminal route facewise conservativity]
\label{thm:streamname-terminal-route-facewise-conservativity}
Let $U$ be an accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request section, and let $P$ be a consumer-visible terminal
presentation of $U$. Suppose $P$ preserves the accepted carrier verdict, the
accepted classifier verdict, and the consumer-facing terminal route of $U$.
Then $P$ restricts facewise to the same terminal $\StreamNameUp$,
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces as $U$, and to the same
displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$ support rows.

No quotient stream equality, host sequence equality, selected limit, countable
choice, ambient $\RealUp$ completeness, metric-completeness datum, aggregate
formalstatus row, or bridge row can serve as a substitute coordinate for this
conservative terminal presentation.
\end{theorem}
\begin{proof}
First exhaust the coordinates that a preserved terminal verdict can use. By
\autoref{thm:streamname-terminal-four-face-support-exhaustion}, every accepted
consumer-visible support coordinate of $U$ is one of the four displayed faces
or one of the displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and
local $\NameCert$ rows.

Assume contrapositively that $P$ does not restrict facewise to this displayed
support. Then it either omits one displayed face or row, or it replaces one of
them by an off-route coordinate. The defect localization theorem
\autoref{thm:streamname-terminal-support-defect-localization} forces such a
failure to appear on a visible face or displayed support row whenever the
carrier verdict, classifier verdict, or terminal route is not preserved.

The hypotheses say that $P$ preserves exactly those three consumer-visible
outputs. Hence no such localized defect is available. The exhaustion theorem
also says that quotient equality, host sequence equality, selected limits,
choice, completeness, aggregate formalstatus, and bridge rows are not accepted
support coordinates, so none of them can repair the missing facewise evidence.

It remains to identify the preserved presentation. Read $P$ and $U$ as two
accepted terminal presentations with the same visible faces and componentwise
replayed support rows. The transport stability theorem
\autoref{thm:streamname-terminal-four-face-support-transport-stability}
therefore identifies their consumer-visible terminal support packets. Thus
preserving the accepted carrier verdict, classifier verdict, and terminal route
is conservative exactly on the four BEDC-visible faces and displayed support
rows listed in the statement.
\end{proof}

\begin{theorem}[StreamName terminal support replay induction]
\label{thm:streamname-terminal-four-face-support-replay-induction}
Let $U$ and $V$ be accepted current Phase $\RealUp$ and Completion terminal
$\StreamNameUp$ request sections. Suppose the replay from $U$ to $V$ begins
with the same finite $\StreamNameUp$ window, and then replays in order the
$\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ visible faces together with
the displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert$ support rows. Then finite induction over this ordered support list
determines one consumer-visible terminal support packet.

The induction uses only those displayed faces and rows. It does not use
quotient stream equality, host sequence equality, selected limits, countable
choice, ambient $\RealUp$ completeness, metric-completeness data, aggregate
formalstatus rows, or bridge rows.
\end{theorem}
\begin{proof}
Start with the displayed finite $\StreamNameUp$ window. The minimality theorem
\autoref{thm:streamname-terminal-four-face-support-minimality} supplies the
base: this window is a required support coordinate and cannot be replaced by
any off-route equality, limit, completeness, formalstatus, or bridge datum.

For the induction step, assume the replayed prefix has already determined the
same terminal support prefix. Adding the next displayed row preserves
determinacy because minimality forbids deleting that row or substituting a
different support coordinate while keeping the same Real-facing and
completion-facing verdicts.

At the $\RegSeqRatUp$ step, the exactness theorem
\autoref{thm:regseqrat-real-terminal-four-face-exactness} identifies the
replayed prefix as the terminal four-face RegSeqRat packet. The source
uniqueness theorem
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness} then rules out a
second finite RegSeqRat source with the same public verdict.

At the final $\RealUp$ step, theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every accepted
current Phase Real and Completion terminal read through the ordered
$\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$--$\RealUp$ route and the
displayed support rows. Thus the induction has exhausted the full terminal
route.

By
\autoref{thm:streamname-terminal-four-face-support-exhaustion}, every accepted
consumer-visible support coordinate is one of these four faces or displayed
rows. The componentwise replay hypotheses therefore give exactly the transport
hypotheses of
\autoref{thm:streamname-terminal-four-face-support-transport-stability}, which
concludes that $U$ and $V$ present one terminal support packet.
\end{proof}

\begin{theorem}[StreamName finite-cover terminal support minimality]
\label{thm:streamname-finite-cover-terminal-support-minimality}
Let $\{Q_i\}_{i \in I}$ be a finite family of accepted current Phase $\RealUp$
and Completion $\StreamNameUp$ request sections. Suppose every accepted overlap
displays the same $\StreamNameUp$ finite-window row, the same
$\DyadicRatCoreUp$ ledger row, the same $\RegSeqRatUp$ readback row, the same
$\RealUp$ seal boundary, and the same $\BHist$, componentwise $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ support rows when read through either local
section. Then the cover-descent terminal support packet for the family is
accepted exactly on those four visible faces and displayed support rows.

Moreover, deleting any one visible face or any one displayed support row
prevents the resulting cover packet from presenting the same carrier verdict
and the same classifier verdict to Real-facing or completion-facing consumers.
This finite-cover minimality claim uses no quotient stream equality, host
sequence equality, selected limits, countable choice, ambient $\RealUp$
completeness, metric-completeness data, aggregate formalstatus rows, or bridge
rows.
\end{theorem}
\begin{proof}
First form the cover surface. Apply
\autoref{thm:streamname-finite-section-cover-descent-classifier-reflection} to
the finite family. The accepted-overlap hypotheses place the carrier verdict
and classifier verdict on the common StreamName finite window, DyadicRatCore
ledger, RegSeqRat readback, Real seal boundary, and the displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next compare all choices of cover presentation. The common-refinement theorem
\autoref{thm:streamname-finite-cover-common-refinement-classifier-uniqueness}
says that any certified finite refinement reads the same public four-face
classifier surface. Thus the cover-descent terminal packet is independent of
the chosen finite presentation once the displayed overlap rows agree.

Now work on each terminal section. For every $i \in I$,
\autoref{thm:streamname-terminal-four-face-support-minimality} says that the
local terminal packet is accepted exactly on the four visible faces and the
displayed support rows, and that deleting any one of these coordinates loses
the same Real-facing or completion-facing verdict. Therefore a shorter cover
packet would already be shorter on some accepted local section or accepted
overlap.

It remains to pass from local minimality to cover minimality. Use
\autoref{thm:streamname-terminal-four-face-support-replay-induction} on the
ordered list consisting of the StreamName finite window, the DyadicRatCore
ledger, the RegSeqRat readback, the Real seal boundary, and the displayed
support rows. The induction transports the local terminal packets through the
cover in the same order and gives one consumer-visible terminal support packet.

Finally rule out substitutes for the missing coordinate. The exactness theorem
\autoref{thm:regseqrat-real-terminal-four-face-exactness} identifies the
RegSeqRat terminal boundary with precisely the four-face support packet, while
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness} rules out a
second finite RegSeqRat source with the same public verdict. The Real exit
totality theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} then forces every
accepted Phase Real and Completion terminal read through the same ordered
route.

The coordinates listed outside the statement are absent from that route.
Hence quotient stream equality, host sequence equality, selected limits,
countable choice, ambient $\RealUp$ completeness, metric-completeness data,
aggregate formalstatus rows, and bridge rows cannot supply the deleted face or
support row, and cannot preserve the same carrier and classifier verdicts.
\end{proof}

\begin{theorem}[StreamName finite-cover terminal support defect localization]
\label{thm:streamname-finite-cover-terminal-support-defect-localization}
Let $\{Q_i\}_{i \in I}$ be a finite family of accepted current Phase
$\RealUp$ and Completion $\StreamNameUp$ request sections satisfying the
accepted-overlap hypotheses of
\autoref{thm:streamname-finite-cover-terminal-support-minimality}. Suppose a
cover-descent terminal support packet for the family fails to preserve the
carrier verdict, the classifier verdict, or the consumer-facing terminal route
presented by that finite cover. Then the failure is witnessed on one local
face among $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$, or on one displayed support row among $\BHist$, componentwise
$\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$.

The witness is componentwise on one accepted local section or accepted
overlap. Quotient stream equality, host sequence equality, selected limits,
countable choice, ambient $\RealUp$ completeness, metric-completeness data,
aggregate formalstatus rows, and bridge rows cannot serve as the defect
carrier and cannot serve as the repair coordinate for the cover-descent
terminal packet.
\end{theorem}
\begin{proof}
First fix the cover support. By
\autoref{thm:streamname-finite-cover-terminal-support-minimality}, the
finite cover presents its terminal support packet exactly on the StreamName
finite-window face, the DyadicRatCore ledger face, the RegSeqRat readback
face, the Real seal face, and the displayed $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows.

Now restrict the failed cover presentation to one accepted local section or
accepted overlap where the carrier verdict, classifier verdict, or terminal
route is lost. Apply
\autoref{thm:streamname-terminal-support-defect-localization} on that local
section. The local theorem places the defect on one of the four visible faces
or on one displayed support row, and excludes quotient, host-sequence, limit,
choice, completeness, aggregate-status, and bridge coordinates.

It remains to show that this local witness is still the cover witness. Use
\autoref{thm:streamname-terminal-four-face-support-replay-induction} on the
ordered cover support list. The induction transports the local localization
through the StreamName window, DyadicRatCore ledger, RegSeqRat readback, Real
seal boundary, and displayed support rows without adding any off-route
coordinate.

At the RegSeqRat face,
\autoref{thm:regseqrat-real-terminal-four-face-exactness} identifies the
transported boundary with the terminal four-face support packet, and
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness} rules out a
second finite RegSeqRat source with the same public verdict. Thus a RegSeqRat
defect cannot be repaired by changing quotient equality, selected limits, or
ambient completeness data.

Finally
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every accepted
current Phase Real and Completion terminal read through the same ordered
$\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$--$\RealUp$ exit route.
The cover-descent packet therefore has no remaining coordinate outside the
four faces and displayed rows on which a carrier verdict, classifier verdict,
or consumer-facing terminal route defect could live.
\end{proof}

\begin{theorem}[StreamName finite-cover terminal support removal witness]
\label{thm:streamname-finite-cover-terminal-support-removal-witness}
Let $\{Q_i\}_{i \in I}$ be a finite family of accepted current Phase
$\RealUp$ and Completion $\StreamNameUp$ request sections satisfying the
accepted-overlap hypotheses of
\autoref{thm:streamname-finite-cover-terminal-support-minimality}. Delete
from the cover-descent terminal support packet either one visible face among
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, or one
displayed support row among $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$,
and local $\NameCert$. Then the shortened cover packet cannot present the same
carrier verdict, classifier verdict, and consumer-facing terminal route as the
original finite cover.

The lost verdict is witnessed on one accepted local section or accepted
overlap. Quotient stream equality, host sequence equality, selected limits,
countable choice, ambient $\RealUp$ completeness, metric-completeness data,
aggregate formalstatus rows, and bridge rows cannot replace the deleted face
or displayed row and cannot repair the cover-descent packet.
\end{theorem}
\begin{proof}
Start with the finite cover support. By
\autoref{thm:streamname-finite-cover-terminal-support-minimality}, every
visible face and displayed row named in the statement is a required coordinate
of the cover-descent terminal packet. Deleting one of those coordinates
therefore removes data needed by the accepted carrier verdict, classifier
verdict, or consumer-facing terminal route.

Now localize the loss. Apply
\autoref{thm:streamname-finite-cover-terminal-support-defect-localization} to
the shortened cover packet. The defect is witnessed on one accepted local
section or accepted overlap, and it lies on a visible
$\StreamNameUp$--$\DyadicRatCoreUp$--$\RegSeqRatUp$--$\RealUp$ face or on one
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or local $\NameCert$ row.

On that local section, use
\autoref{thm:streamname-terminal-support-removal-witness}. The local deletion
already prevents presentation of the same carrier verdict, classifier verdict,
and consumer-facing terminal route, with the witness read as a finite
request-section mismatch.

It remains to transport the local loss back through the cover. Use
\autoref{thm:streamname-terminal-four-face-support-replay-induction} on the
ordered cover support list. The induction replays the local witness through
the StreamName finite window, DyadicRatCore ledger, RegSeqRat readback, Real
seal boundary, and displayed support rows, so the cover cannot regain the lost
terminal packet from another section of the same family.

Finally rule out substitutes. The exactness theorem
\autoref{thm:regseqrat-real-terminal-four-face-exactness} identifies the
RegSeqRat boundary with precisely the four-face terminal support packet, and
\autoref{thm:regseqrat-terminal-four-face-source-uniqueness} rules out a
second finite RegSeqRat source with the same public verdict. The Real exit
totality theorem
\autoref{thm:real-l10-dependency-lattice-exit-totality} sends every accepted
current Phase Real and Completion terminal read through the same ordered
route.

Thus quotient stream equality, host sequence equality, selected limits,
countable choice, ambient $\RealUp$ completeness, metric-completeness data,
aggregate formalstatus rows, and bridge rows are off-route for this finite
cover. They cannot supply the deleted coordinate and cannot preserve the same
carrier verdict, classifier verdict, and consumer-facing terminal route.
\end{proof}
