\section{StreamName terminal window fusion}
\label{sec:streamname-terminal-window-fusion}

\begin{theorem}[StreamName Real-completion terminal-window fusion]
\label{thm:streamname-real-completion-terminal-window-fusion}
Every accepted Phase Real and Completion read through
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
is determined by the fused terminal window consisting of the StreamName finite request window, the $\DyadicRatCoreUp$ tolerance ledger, the $\RegSeqRatUp$ readback, the $\RealUp$ seal, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Equivalently, two accepted reads with the same fused terminal window have the same public classifier surface and the same terminal factorization through the four Real and Completion exit faces.

The fused packet exports no quotient stream equality, no host sequence equality, no selected limit, no ambient $\RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
\end{theorem}
\begin{proof}
Begin with the four-object exit route of \autoref{thm:streamname-real-completion-four-object-exit-route}. It identifies every accepted current read with the four displayed faces and with only the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Next apply the terminal pullback and terminal exactness results, \autoref{thm:streamname-real-completion-four-object-terminal-pullback} and \autoref{thm:streamname-real-completion-four-object-terminal-exactness}. These results say that agreement on the StreamName finite request window, the DyadicRatCore tolerance ledger, the RegSeqRat readback, the RealUp seal, and the displayed support rows is precisely the terminal boundary for public acceptance.

Now transport this terminal boundary to the classifier surface. Use \autoref{thm:streamname-real-completion-classifier-pullback}: once the fused terminal window agrees componentwise, the public classifier has no second coordinate on which to distinguish the two reads.

It remains to bind the dependency and handoff rows. The dependency exactness theorem \autoref{thm:streamname-real-completion-dependency-exactness} names the same four faces as necessary and sufficient, while \autoref{thm:streamname-real-completion-three-touchpoint-handoff-route} reads the StreamName finite-window handoff, DyadicRatCore ledger handoff, and RegSeqRat-to-Real seal as route witnesses for those existing rows.

Finally apply the no-choice route factorization, \autoref{thm:streamname-real-completion-route-no-choice-factorization}. It removes every attempted selector, quotient, completeness, metric, choice, or bridge coordinate from the packet. Therefore the fused terminal window determines the accepted Phase Real and Completion read exactly through the four displayed exit faces and the five displayed support rows.
\end{proof}

\begin{theorem}[StreamName terminal fusion common-refinement stability]
\label{thm:streamname-terminal-fusion-common-refinement-stability}
Let $\mathcal W_L$ and $\mathcal W_R$ be accepted Phase Real and Completion reads whose $\StreamNameUp$ finite windows admit a certified common refinement $\mathcal R$. Suppose the refinement transports the same $\DyadicRatCoreUp$ tolerance ledger, the same $\RegSeqRatUp$ readback, the same $\RealUp$ seal, and the same displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then the fused terminal-window packet read through $\mathcal W_L$ is the same packet read through $\mathcal W_R$. In particular the public classifier surface is unchanged by passing to $\mathcal R$ and restricting back to either selected window.

The stability statement adds no quotient stream equality, no host sequence equality, no selected limit, no ambient $\RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
\end{theorem}
\begin{proof}
First read the common refinement at the StreamName boundary. Apply \autoref{thm:streamname-finite-window-common-refinement-export} and \autoref{thm:streamname-common-refinement-source-determinacy}. The refinement $\mathcal R$ supplies one finite-window classifier, one $\mathsf{ProbeBundle}$ row, the same $\mathsf{InBundle}$ membership rows, the same selected histories, and the same displayed $\hsame/\Cont/\Pkg$ ledger rows for both selected windows.

Next pass from the source tuple to the Real and Completion exit packet. Use \autoref{thm:streamname-common-refinement-public-exactness}: every downstream $\RegSeqRat$ handoff and every finite-window $\RealUp$ handoff read from $\mathcal R$ factors through that common source tuple. The hypotheses identify the $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, and local $\NameCert$ rows as the same transported data on the two restrictions.

Now apply the terminal pullback theorem \autoref{thm:streamname-real-completion-four-object-terminal-pullback}. Since the four faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ and the displayed support rows agree after transport along $\mathcal R$, the two accepted reads determine the same terminal finite BEDC pullback. The terminal-window fusion theorem \autoref{thm:streamname-real-completion-terminal-window-fusion} repacks this pullback as one fused terminal-window packet.

Finally transport the equality of terminal packets to the public classifier surface by \autoref{thm:streamname-real-completion-classifier-pullback}. The no-choice route factorization \autoref{thm:streamname-real-completion-route-no-choice-factorization} removes every selector, quotient, completeness, metric, choice, and bridge coordinate, so a common refinement cannot create a second public presentation of the same terminal route.
\end{proof}

\begin{theorem}[StreamName terminal fusion common-tail Real boundary pullback]
\label{thm:streamname-terminal-fusion-common-tail-real-boundary-pullback}
Let $\mathcal W$ be an accepted Phase Real and Completion read, and let its fused terminal window be transported through a $\RegSeqRatUp$ common-tail window packet with common refinement $W_\ast$. The transported fused terminal packet determines exactly the same public $\RealUp$ seal boundary as the common-tail Real boundary equivalence of \autoref{thm:regseqrat-common-tail-real-boundary-equivalence}.

Equivalently, two such transported reads have the same public classifier surface if and only if they agree on the $\StreamNameUp$ finite window, the $\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the $\RegSeqRatUp$ classifier and regularity rows, the $\RealUp$ seal-source rows, and the displayed rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
No quotient stream equality, host sequence equality, selected limit, ambient $\RealUp$ completeness theorem, metric-completeness datum, countable-choice row, or standard bridge row is part of this pullback boundary.
\end{theorem}
\begin{proof}
First use \autoref{thm:streamname-terminal-fusion-common-refinement-stability}. The common refinement makes the selected $\StreamNameUp$ finite windows one fused terminal packet after the shared $\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the $\RegSeqRatUp$ readback rows, the $\RealUp$ seal, and the displayed support rows have been transported through $W_\ast$.

Next apply \autoref{thm:regseqrat-common-tail-real-boundary-equivalence}. The common-tail packet and the finite-request $\RealUp$ seal boundary determine one another exactly on the StreamName schedule and refinement rows, the dyadic endpoint-radius-distance ledger, the RegSeqRat classifier and regularity rows, the Real seal-source rows, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Now compare this boundary with the four-face public interface. By \autoref{thm:real-l10-four-face-finite-pullback-public-interface}, those same finite rows form the public pullback surface over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Thus the common-tail presentation cannot add or remove a public row from the fused terminal presentation.

Finally transport the shared four-face surface to the public classifier by \autoref{thm:streamname-real-completion-classifier-pullback}. Agreement on the displayed rows is therefore sufficient for public classifier agreement, and any public classifier agreement reads back to the same displayed rows through the common-tail Real boundary equivalence. The no-choice factorization of \autoref{thm:streamname-real-completion-route-no-choice-factorization} excludes selectors, quotient stream equality, host sequence equality, chosen limits, completeness, metric-completeness data, countable choice, and bridge rows from serving as another boundary coordinate.
\end{proof}

\begin{theorem}[StreamName terminal fusion finite-request section exactness]
\label{thm:streamname-terminal-fusion-finite-request-section-exactness}
Let $\mathcal W$ be an accepted fused terminal-window packet for the
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ route, and view its
terminal request as a finite-request section. Then the displayed rows of
$\mathcal W$ are exactly the finite-request section pullback rows: the
$\StreamNameUp$ finite window, the $\DyadicRatCoreUp$ endpoint, radius, and
distance ledger, the $\RegSeqRatUp$ classifier, regularity, and readback rows,
the $\RealUp$ seal-source rows, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

Conversely, any finite-request section carrying precisely those displayed rows
determines the same fused terminal-window packet on the public terminal
four-face route.

This identification exports no quotient stream equality, no host sequence
equality, no selected limit, no ambient completeness row, no
metric-completeness data, no countable-choice row, and no bridge row.
\end{theorem}
\begin{proof}
For the forward direction, first read $\mathcal W$ through
\autoref{thm:streamname-real-completion-terminal-window-fusion}. The fused
terminal packet is exhausted by the finite StreamName window, the DyadicRatCore
ledger, the RegSeqRat readback, the Real seal, and the displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows.

Next view the same request as a finite-request section and apply
\autoref{thm:streamname-finite-request-section-pullback}. This identifies the
section with the same StreamName finite schedule, DyadicRatCore endpoint,
radius, and distance ledger, RegSeqRat classifier and regularity/readback
rows, Real seal-source rows, and support provenance.

For the reverse direction, start with a finite-request section carrying those
rows. Apply
\autoref{thm:streamname-finite-request-section-classifier-pullback} to recover
the public carrier and classifier verdict on the terminal four-face route.
Then apply
\autoref{thm:streamname-terminal-fusion-common-tail-real-boundary-pullback} to
repack the same row family as the common-tail Real boundary of one fused
terminal packet.

Finally use \autoref{thm:streamname-finite-request-section-nonescape}. It
removes quotient stream equality, host sequence equality, selected limits,
ambient completeness, metric-completeness data, countable choice, and bridge
rows from the section surface. Hence the finite-request section and the fused
terminal-window packet are interchangeable exactly on the displayed BEDC-visible
L10 rows.
\end{proof}

\begin{theorem}[StreamName terminal fusion source exhaustion]
\label{thm:streamname-terminal-window-fusion-source-exhaustion}
Every accepted current Phase Real and Completion read whose terminal request is
presented as a fused $\StreamNameUp$ window factors through exactly the four
faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
and exactly the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Conversely, a terminal request carrying those four faces and those five support
rows determines the same public finite-request section as the fused terminal
window presentation.

The source-exhaustion statement exports no quotient stream equality, no host
sequence equality, no selected limit, no ambient $\RealUp$ completeness theorem,
no metric-completeness data, no countable-choice row, and no bridge row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:streamname-real-completion-terminal-window-fusion}. It
identifies an accepted current read with the fused terminal packet over the
StreamName finite request window, the DyadicRatCore tolerance ledger, the
RegSeqRat readback, the Real seal, and the displayed support rows.

Next apply
\autoref{thm:streamname-terminal-fusion-finite-request-section-exactness}. The
finite-request section exposes exactly the same four faces and exactly the same
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows, and no further public row is
available on the section surface.

For the reverse direction, start with a terminal request carrying the displayed
faces and support rows. Use
\autoref{thm:streamname-terminal-fusion-common-tail-real-boundary-pullback} to
read those rows as the common-tail $\RealUp$ boundary of the fused terminal
presentation, and then read the resulting packet back through finite-request
section exactness.

Finally apply
\autoref{thm:streamname-real-completion-route-no-choice-factorization}. Quotient
stream equality, host sequence equality, selected limits, ambient completeness,
metric-completeness data, countable choice, and bridge rows have no coordinate
in the route, so the four displayed faces and the five support rows exhaust the
accepted current source.
\end{proof}

\begin{theorem}[StreamName terminal-window fusion reindexing compatibility]
\label{thm:streamname-terminal-window-fusion-reindexing-compatibility}
Let $\mathcal W_0$ and $\mathcal W_1$ be accepted Phase Real and Completion
terminal-window packets. Suppose they differ only by a certified public
$\StreamNameUp$ finite-window reindex route, and suppose that route transports
componentwise the $\DyadicRatCoreUp$ tolerance ledger, the $\RegSeqRatUp$
readback rows, the $\RealUp$ seal row, the displayed $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ support rows, and the public endpoint rows.
Then $\mathcal W_0$ and $\mathcal W_1$ determine the same fused
terminal-window packet and the same public four-face route through
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp.
$$

Conversely, any fused terminal-window packet transported by the certified
identity reindexer or by a composable certified reindexer reads back to the
same public finite observation section. The compatibility claim introduces no
quotient stream equality, host sequence equality, selected limit,
countable-choice row, ambient $\RealUp$ completeness, metric-completeness
datum, or standard bridge row.
\end{theorem}
\begin{proof}
First identify the finite public section. Apply
\autoref{thm:streamname-window-reindex-determinacy} to the two displayed
$\StreamNameUp$ finite-window packets. The certified reindex route supplies the
$\hsame$-compatible map, the common endpoint rows, and the componentwise
transport of the displayed $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so
both packets expose one public finite observation section.

Next carry that section to the terminal L10 route. Use
\autoref{thm:streamname-reindex-terminal-coverage}. The transported finite
section presents the same $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance
ledger, $\RegSeqRatUp$ readback, and $\RealUp$ seal as the terminal Phase Real
and Completion route.

Now repack the transported rows as a fused terminal packet. Apply
\autoref{thm:streamname-real-completion-terminal-window-fusion} to read the
common four-face route as one fused terminal-window packet, and apply
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion} to see that
no source coordinate remains beyond the four faces and the displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows.

For the converse, read an identity-reindexed or composably reindexed fused
packet through the same terminal coverage theorem. Identity and composable
certified reindexers return the same finite observation section before fusion,
and the fusion and source-exhaustion theorems repack exactly that section as
the same public terminal route.

The exclusions follow because every step is confined to the displayed
finite-window route, the transported tolerance ledger, the readback rows, the
seal row, and the named support rows. None of the cited results exports
quotient stream equality, host sequence equality, selected limits,
countable-choice data, ambient completeness, metric-completeness data, or a
standard bridge row.
\end{proof}

\begin{theorem}[StreamName terminal fusion finite-cover cocycle exactness]
\label{thm:streamname-terminal-fusion-finite-cover-cocycle-exactness}
Let $\{\mathcal W_i\}_{i\in I}$ be a finite family of certified $\StreamNameUp$ windows. Suppose the pairwise windows $\mathcal W_{ij}$ and triple windows $\mathcal W_{ijk}$ carry the pasted-source hypotheses for finite StreamName--$\RegSeqRatUp$ covers, each local terminal fused packet transports through a $\RegSeqRatUp$ common-tail packet, and every local handoff row consumes the same $\DyadicRatCoreUp$ endpoint, radius, and distance ledger together with the same $\RealUp$ seal-source row.

Then the family pastes to one terminal fused packet exactly when the pairwise restrictions expose the same common-tail Real boundary. The pasted packet has precisely the visible rows
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
where the $\StreamNameUp$ rows are the given finite windows, the $\DyadicRatCoreUp$ rows are the endpoint, radius, and distance ledger, the $\RegSeqRatUp$ rows are the common-tail classifier and regularity rows, and the $\RealUp$ row is the seal-source row. Its only support provenance is
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

The exactness claim exports no quotient stream equality, no host sequence equality, no selected limit, no ambient $\RealUp$ completeness theorem, no metric-completeness datum, no countable-choice row, and no standard bridge row.
\end{theorem}
\begin{proof}
First build the finite StreamName source surface. Apply \autoref{thm:streamname-regseqrat-finite-cover-pasted-source-exhaustion} to the certified windows and their pairwise and triple overlap data. This produces one pasted finite source whose support rows remain the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Next transport every local fused packet through the common-tail boundary. By \autoref{thm:regseqrat-common-tail-real-boundary-equivalence}, the $\RegSeqRatUp$ common-tail classifier and regularity rows expose exactly the same Real seal-source boundary as the dyadic endpoint, radius, and distance ledger carried by the local handoff rows.

Now apply \autoref{thm:real-finite-cover-seal-pasting-criterion}. The common-tail Real boundary is therefore the cocycle condition for pasting the local $\RealUp$ seal-source rows across the finite cover, and the shared $\DyadicRatCoreUp$ ledger prevents a second radius or distance coordinate from entering the seal.

Finally use \autoref{thm:streamname-terminal-fusion-common-tail-real-boundary-pullback}. It identifies agreement of the pairwise common-tail Real boundaries with agreement of the terminal fused StreamName packet on the four visible faces and the five support rows. Hence the local terminal fused packets paste to one terminal fused packet exactly in the stated case, while quotient stream equality, host sequence equality, chosen limits, completeness, metric-completeness data, countable choice, and bridge rows remain outside the boundary.
\end{proof}

\begin{theorem}[StreamName terminal fusion cocycle section descent]
\label{thm:streamname-terminal-fusion-cocycle-section-descent}
Let $\{\mathcal W_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows satisfying the pasted-source hypotheses of
\autoref{thm:streamname-terminal-fusion-finite-cover-cocycle-exactness}.
Assume each local fused terminal packet is carried through the same
$\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the same
$\RegSeqRatUp$ common-tail classifier and regularity rows, and the same
$\RealUp$ seal-source row. Then pairwise common-tail $\RealUp$ boundary
agreement is equivalent to descent of the local fused terminal packets to one
finite-request section.

The descended section has exactly the visible rows consisting of the
$\StreamNameUp$ windows, the $\DyadicRatCoreUp$ endpoint, radius, and distance
ledger, the $\RegSeqRatUp$ common-tail classifier and regularity rows, the
$\RealUp$ seal-source row, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
It exports no quotient stream equality, no host sequence equality, no selected
limit, no countable-choice row, no ambient $\RealUp$ completeness theorem, no
metric-completeness datum, and no standard bridge row.
\end{theorem}
\begin{proof}
For the descent direction, apply
\autoref{thm:streamname-terminal-fusion-finite-cover-cocycle-exactness}. The
pairwise common-tail $\RealUp$ boundary agreement is exactly the cocycle
condition for the certified local terminal packets to paste to one fused
terminal packet over the finite family.

Next read the pasted terminal packet as a finite request. Use
\autoref{thm:streamname-finite-request-section-pullback}. The pullback exposes
precisely the StreamName windows, the DyadicRatCore endpoint-radius-distance
ledger, the RegSeqRat classifier and regularity rows, the Real seal-source
row, and the displayed $\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows.
Thus the pasted packet descends to one finite-request section with no further
public coordinate.

For the reverse direction, start with such a finite-request section. The
section pullback gives the same displayed rows on every local window, and
\autoref{thm:regseqrat-common-tail-real-boundary-equivalence} identifies those
rows with the common-tail $\RealUp$ boundary read by the RegSeqRat classifier
and regularity data.

Finally apply \autoref{thm:real-finite-cover-seal-pasting-criterion} and then
\autoref{thm:streamname-terminal-fusion-common-tail-real-boundary-pullback}.
The first theorem reads the shared boundary as the finite-cover seal pasting
criterion, while the second reads it back as agreement of the local fused
StreamName terminal packets on exactly the visible rows and the five support
rows. The excluded quotient, host-sequence, selected-limit, choice,
completeness, metric-completeness, and bridge rows therefore cannot be part of
the descent datum.
\end{proof}

\begin{theorem}[StreamName terminal fusion refinement invariance]
\label{thm:streamname-terminal-fusion-refinement-invariance}
Let $\{\mathcal W_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows satisfying the hypotheses of
\autoref{thm:streamname-terminal-fusion-cocycle-section-descent}. Suppose
$\{\mathcal R_a\}_{a\in A}$ is a certified finite refinement of that family
whose restrictions preserve the same $\DyadicRatCoreUp$ endpoint, radius, and
distance ledger, the same $\RegSeqRatUp$ common-tail classifier and regularity
rows, the same $\RealUp$ seal-source row, and the same support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then the finite-request section descended from the refined family is the same
section descended from the original family. Consequently the public terminal
fused packet over the four faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
is unchanged by passing to the certified refinement and restricting back to the
original cover.

The invariant packet exports no quotient stream equality, no host sequence
equality, no selected limit, no countable-choice row, no ambient $\RealUp$
completeness theorem, no metric-completeness datum, and no standard bridge row.
\end{theorem}
\begin{proof}
First compare each original window with its refined restrictions. Apply
\autoref{thm:streamname-terminal-fusion-common-refinement-stability}. The
preserved endpoint-radius-distance ledger, common-tail classifier and
regularity rows, seal-source row, and displayed support rows make every
restriction read the same terminal fused packet as the original window from
which it is certified.

Next verify the cocycle on the refined cover. Use
\autoref{thm:regseqrat-common-tail-triple-overlap-cocycle} to identify the
triple-overlap RegSeqRat common-tail rows, and then apply
\autoref{thm:streamname-terminal-fusion-finite-cover-cocycle-exactness}. The
pairwise common-tail $\RealUp$ boundary condition for the refined windows is
therefore the same finite-cover cocycle condition as for the original family.

Now descend both finite covers. By
\autoref{thm:streamname-terminal-fusion-cocycle-section-descent}, the original
family and the certified refinement each produce one finite-request section
carrying exactly the displayed $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows.

Finally restrict the refined section back along the refinement maps. The
common-refinement stability already identifies every restricted local terminal
packet with its original local packet, while the finite-cover cocycle
exactness identifies the pasted packet by precisely those rows. Hence the two
descended sections are the same finite-request section, and the public
terminal fused packet is invariant under the certified refinement. Since all
steps read only the visible four faces and the five support rows, quotient
stream equality, host sequence equality, selected limits, choice,
completeness, metric-completeness data, and bridge rows remain outside the
interface.
\end{proof}

\begin{theorem}[StreamName terminal fusion phase-exit consumer readback]
\label{thm:streamname-terminal-fusion-phase-exit-consumer-readback}
Let $\mathcal W$ be an accepted fused StreamName terminal-window packet over
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
with support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
If a same-route $\RealCompletionExactBoundaryUp$ face is supplied for the four
roadmap faces of $\mathcal W$, then $\mathcal W$ determines the same five-face
consumer readback as an accepted $\PhaseRealCompletionExitUp$ consumer: the
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and
$\RealCompletionExactBoundaryUp$ local records, together with the supporting
$\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local
$\NameCert_{\PhaseRealCompletionExitUp}$ rows.

Conversely, any accepted $\PhaseRealCompletionExitUp$ consumer displaying
precisely those five local records and those support rows restricts along the
four roadmap faces to the fused StreamName finite-window packet carried by
$\mathcal W$.

The comparison exports no quotient stream equality, no selected limit, no host
completeness row, no countable-choice row, no metric-completeness row, no
aggregate formalstatus row, no bridge token, and no fused completion witness.
\end{theorem}
\begin{proof}
For the forward direction, first apply
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion}. It reads
the accepted fused terminal-window packet through exactly the four roadmap
faces and the displayed $\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows.

Next apply
\autoref{thm:streamname-terminal-fusion-finite-request-section-exactness}.
The same row family is the finite-request section surface, so supplying
$\RealCompletionExactBoundaryUp$ on that same finite route adds the fifth
local face without changing the four-face StreamName packet.

Finally apply
\autoref{thm:phase-real-completion-exit-facewise-consumer-readback}. Its
consumer theorem reads exactly the five local records and the same support
rows, with the exact-boundary face constrained to the four roadmap faces.
Thus the fused terminal packet determines the phase-exit consumer readback.

For the reverse direction, start with an accepted
$\PhaseRealCompletionExitUp$ consumer displaying those five local records.
The facewise readback theorem identifies the first four records as the dyadic,
stream, regular-rational, and real faces on the same finite route as the
exact-boundary face.

Discard the exact-boundary face and keep the displayed support rows. By source
exhaustion and finite-request section exactness, those four roadmap faces and
support rows are precisely the fused StreamName finite-window packet. The
excluded quotient, selected-limit, host-completeness, choice,
metric-completeness, aggregate-status, bridge, and fused-witness rows therefore
cannot supply another consumer coordinate.
\end{proof}

\begin{theorem}[StreamName terminal fusion phase-exit refinement readback invariance]
\label{thm:streamname-terminal-fusion-phase-exit-refinement-readback-invariance}
Let $\{\mathcal W_i\}_{i\in I}$ be a finite family of certified
$\StreamNameUp$ windows satisfying the hypotheses of
\autoref{thm:streamname-terminal-fusion-cocycle-section-descent}, and let
$\{\mathcal R_a\}_{a\in A}$ be a certified finite refinement preserving the
same $\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the same
$\RegSeqRatUp$ common-tail classifier and regularity rows, the same $\RealUp$
seal-source row, and the same support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Assume moreover that the original descended packet and the refined descended
packet are supplied with a same-route $\RealCompletionExactBoundaryUp$ face for
their four roadmap faces. Then the accepted $\PhaseRealCompletionExitUp$
consumer readback obtained from the refined fused terminal packet is the same
five-face readback as the one obtained from the original fused terminal packet:
the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and
$\RealCompletionExactBoundaryUp$ local records, together with the supporting
$\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local
$\NameCert_{\PhaseRealCompletionExitUp}$ rows.

The comparison exports no quotient stream equality, no host sequence equality,
no selected limit, no countable-choice row, no ambient $\RealUp$ completeness
theorem, no metric-completeness datum, no aggregate formalstatus row, no
bridge token, and no fused completion witness.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-terminal-fusion-refinement-invariance}. The certified
refinement preserves exactly the endpoint-radius-distance ledger, common-tail
classifier and regularity rows, seal-source row, and displayed support rows
used by the descent theorem. Hence the original cover and the refined cover
descend to the same finite-request section and to the same public fused
terminal packet over the four faces.

Next read the original presentation as a phase-exit consumer. Apply
\autoref{thm:streamname-terminal-fusion-phase-exit-consumer-readback} to the
original fused packet and its same-route $\RealCompletionExactBoundaryUp$
face. The theorem returns precisely the five local records and the displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert_{\PhaseRealCompletionExitUp}$ support
rows.

Apply the same consumer-readback theorem to the refined presentation. The
first step identifies the refined four-face fused packet with the original
four-face fused packet, and the hypothesis supplies the same-route
$\RealCompletionExactBoundaryUp$ face. Therefore the refined presentation
reads back the same five local records and the same support rows.

The no-quotient, no-choice, no-host-completeness, no-metric-completeness,
no-aggregate-status, no-bridge, and no-fused-witness exclusions are inherited
from the refinement-invariance and phase-exit consumer-readback theorems.
Since both applications use only the visible four roadmap faces, the exact
boundary face on that route, and the five displayed support rows, no additional
consumer coordinate is available.
\end{proof}

\begin{theorem}[StreamName terminal fusion universal consumer normal form]
\label{thm:streamname-terminal-fusion-universal-consumer-normal-form}
Let $\mathcal W$ be an accepted terminal fused StreamName packet supplied with a
same-route $\RealCompletionExactBoundaryUp$ face, so that it is readable as an
accepted terminal $\PhaseRealCompletionExitUp$ consumer. Every downstream
consumer of this terminal Phase Real and Completion packet that preserves
BEDC-visible public rows factors through the four roadmap faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
on that route, the same-route $\RealCompletionExactBoundaryUp$ face, and the
support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Equivalently, once the four roadmap faces, the exact-boundary face on that
route, and the displayed support rows are fixed, the consumer readback is in
normal form: two presentations with the same displayed rows give the same
downstream consumer readback.

This normal form exports no quotient stream equality, no host sequence
equality, no selected limit, no ambient completeness row, no metric-completeness
datum, no countable-choice row, no bridge token, no aggregate formalstatus row,
and no fused completion witness.
\end{theorem}
\begin{proof}
First reduce the terminal packet to its source rows. By
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion}, an accepted
terminal fused StreamName packet is exhausted by the four roadmap faces and the
displayed $\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows. Thus a
BEDC-visible downstream consumer cannot read an additional StreamName-side
coordinate before the phase-exit face is attached.

Next attach the same-route exact-boundary face and read the result as a
phase-exit consumer. Apply
\autoref{thm:streamname-terminal-fusion-phase-exit-consumer-readback}. The
consumer readback consists of the four roadmap records, the
$\RealCompletionExactBoundaryUp$ face constrained to that route, and the same
support rows; the excluded quotient, limit, choice, completeness, aggregate
status, bridge, and fused-witness rows are not part of the exported interface.

It remains to check independence from presentation. If two terminal
presentations display the same four roadmap faces, the same exact-boundary face
on that route, and the same support rows, then apply
\autoref{thm:streamname-terminal-fusion-phase-exit-refinement-readback-invariance}
to any certified common refinement between them. The refined and original
presentations give the same five-face phase-exit consumer readback, hence the
same downstream readback for every row-preserving consumer.

Finally identify the roadmap substrate. By
\autoref{thm:streamname-l10-four-face-exit-gate}, the only roadmap faces
available to the terminal route are $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$. The four-face route supplies the roadmap
substrate, while the phase-exit consumer readback retains the
$\RealCompletionExactBoundaryUp$ face as a constrained fifth local record.
Combining that gate with source exhaustion, phase-exit readback, and refinement
readback invariance gives the stated universal normal form.
\end{proof}

\begin{theorem}[StreamName terminal fusion universal consumer reflection]
\label{thm:streamname-terminal-fusion-universal-consumer-reflection}
Let $\mathcal W$ and $\mathcal W'$ be accepted terminal fused StreamName packets
whose four roadmap faces are supplied with same-route
$\RealCompletionExactBoundaryUp$ faces, and suppose their row-preserving
terminal $\PhaseRealCompletionExitUp$ consumer readbacks agree. Then the
displayed terminal rows of the two packets agree: the four roadmap faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
the same-route $\RealCompletionExactBoundaryUp$ face, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert
$$
are the same on both terminal presentations.

Thus consumer equivalence for accepted terminal fused StreamName packets is
reflected exactly by the BEDC-visible four-face terminal surface and its
exact-boundary support. Quotient stream equality, selected limits, host sequence
equality, ambient completeness, metric-completeness, countable choice, aggregate
formalstatus, bridge token, and fused completion witness cannot witness
consumer equality.
\end{theorem}
\begin{proof}
First put each terminal packet in universal consumer normal form. Apply
\autoref{thm:streamname-terminal-fusion-universal-consumer-normal-form} to
$\mathcal W$ and to $\mathcal W'$. Every row-preserving terminal consumer of
either packet factors through its four roadmap faces, same-route
$\RealCompletionExactBoundaryUp$ face, and displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ rows.

Next read both normal forms through the phase-exit interface. By
\autoref{thm:streamname-terminal-fusion-phase-exit-consumer-readback}, the
terminal $\PhaseRealCompletionExitUp$ consumer readback is exactly the five
local faces together with the displayed support rows. Since the two consumer
readbacks agree by hypothesis, the five local records and support rows named by
that theorem agree.

It remains to rule out hidden witnesses. Source exhaustion,
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion}, identifies
the StreamName terminal packet before the exact-boundary attachment with only
the four roadmap faces and the displayed support rows.

Finally apply the no-choice route factorization,
\autoref{thm:streamname-real-completion-route-no-choice-factorization}. It
removes quotient stream equality, selected limits, host sequence equality,
ambient completeness, metric-completeness, countable choice, aggregate
formalstatus, bridge token, and fused completion witness from the terminal
route. Therefore no excluded coordinate can account for the common consumer
readback, and the agreement reflects back exactly to the displayed terminal
rows.
\end{proof}

\begin{theorem}[StreamName terminal fusion four-face exit status equivalence]
\label{thm:streamname-terminal-fusion-four-face-exit-status-equivalence}
Let $\mathcal W$ and $\mathcal W'$ be accepted terminal fused StreamName packets
whose four roadmap faces are supplied with same-route
$\RealCompletionExactBoundaryUp$ faces. Row-preserving terminal
$\PhaseRealCompletionExitUp$ consumer equivalence between $\mathcal W$ and
$\mathcal W'$ holds if and only if their terminal presentations agree on the
four roadmap faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
on the same-route exact-boundary face, and on the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Thus the terminal exit status for the four-object Real-completion route is
exactly the equality class of these BEDC-visible rows.

The equivalence has no further coordinates: aggregate formalstatus, bridge
token, quotient stream equality, selected limits, host sequence equality,
ambient completeness, metric completeness, countable choice, and fused
completion witnesses are not part of the exit-status comparison.
\end{theorem}
\begin{proof}
Assume first that the displayed terminal rows agree. Put each packet in normal
form by
\autoref{thm:streamname-terminal-fusion-universal-consumer-normal-form}. Since
the two packets have the same four roadmap faces, the same same-route
$\RealCompletionExactBoundaryUp$ face, and the same
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows, the normal forms determine
the same row-preserving terminal $\PhaseRealCompletionExitUp$ consumer readback.

For the reverse direction, assume that the row-preserving terminal consumer
readbacks agree. Apply
\autoref{thm:streamname-terminal-fusion-universal-consumer-reflection}. The
reflection theorem reads the common consumer back to equality of the four
roadmap faces, the same-route exact-boundary face, and the displayed support
rows.

It remains to identify the allowed surface. Source exhaustion,
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion}, says that
the accepted terminal fused StreamName packet supplies no StreamName-side
coordinate beyond the four roadmap faces and the displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ rows. The four-face exit gate,
\autoref{thm:streamname-l10-four-face-exit-gate}, fixes the roadmap surface as
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, while
\autoref{thm:streamname-terminal-fusion-phase-exit-consumer-readback} records
the same-route $\RealCompletionExactBoundaryUp$ face as the constrained local
readback for that route.

Finally apply the no-choice route factorization,
\autoref{thm:streamname-real-completion-route-no-choice-factorization}. The
aggregate formalstatus, bridge token, quotient stream equality, selected
limits, host sequence equality, ambient completeness, metric completeness,
countable choice, and fused completion witness are not consumer coordinates on
this terminal route. Therefore the two implications above form the exact
four-face exit status equivalence.
\end{proof}

\begin{theorem}[StreamName terminal fusion support minimality]
\label{thm:streamname-terminal-fusion-support-minimality}
Let $\mathcal W$ be an accepted terminal fused StreamName packet. Deleting any
one roadmap face
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
or any one displayed support row
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert
$$
destroys the accepted terminal packet. Equivalently, no proper subpacket of
these four faces and five support rows carries the same terminal
$\PhaseRealCompletionExitUp$ consumer readback.

There is no replacement row for the missing support: quotient stream equality,
selected limits, countable choice, a metric-completeness row, and bridge rows
are outside the accepted terminal surface.
\end{theorem}
\begin{proof}
The terminal-window fusion theorem
\autoref{thm:streamname-real-completion-terminal-window-fusion} constructs the
accepted packet from exactly the four Real-completion faces and the displayed
support rows. Thus each listed coordinate is part of the packet admitted by the
terminal fusion surface.

Finite-request section exactness,
\autoref{thm:streamname-terminal-fusion-finite-request-section-exactness},
shows that each terminal request is read through the displayed finite section,
so deleting one face or support row removes a row needed by some accepted
finite request. Source exhaustion,
\autoref{thm:streamname-terminal-window-fusion-source-exhaustion}, then rules
out any additional StreamName-side coordinate from filling the gap.

Finally apply the four-face exit status equivalence
\autoref{thm:streamname-terminal-fusion-four-face-exit-status-equivalence}.
The terminal consumer status is exactly the equality class of the four roadmap
faces, the same-route exact-boundary face, and the displayed support rows. A
proper subpacket therefore cannot have the same accepted terminal status, and
the excluded quotient, choice, metric-completeness, and bridge coordinates
cannot provide a substitute.
\end{proof}
