\chapter{Markov-Kakutani Fixed Point NameCert Construction}
\label{ch:concrete-instances-markov-kakutani-fixed-point-namecert}
\origin{human}

Following Markov and Kakutani, the $\MarkovKakutaniFixedPointUp$ packet records the finite BEDC surface for a commuting affine family acting on a compact convex carrier. It is anchored by the convex carrier of \autoref{ch:concrete-instances-convexset-namecert}, the functional-analysis ambient rows of \autoref{ch:concrete-instances-functionalanalysis-namecert}, the compact-convex self-map handoff of \autoref{ch:concrete-instances-schauder-fixed-point-namecert}, and the set-valued fixed-point surface of \autoref{ch:concrete-instances-kakutani-fixed-point-namecert}. The packet names a finite common fixed-point obligation route; it does not import a host compactness theorem, a global choice selector, an ambient locally convex space, or a completed real vector topology outside the displayed rows.

\begin{definition}[Markov-Kakutani fixed point carrier]\label{def:markov-kakutani-fixed-point-carrier}
A $\MarkovKakutaniFixedPointUp$ carrier is a finite $\BHist$ packet
$$
M=(D,A,F,C,W,I,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the compact convex domain row, read through the carried $\ConvexSetUp$ and compact support surfaces.
\item $A$ is the affine ambient row, exposing only the finite vector-operation and scalar-stability data required by the displayed family.
\item $F$ is the commuting-family row, listing the finite subfamily of affine self-maps and their source and target admissions.
\item $C$ is the commutation ledger, recording pairwise commutation only for the displayed finite family windows.
\item $W$ is the finite fixed-window row, recording the common approximate fixed rows inspected by downstream consumers.
\item $I$ is the invariant-subcarrier row, exposing the finite intersection handoff used to keep the common fixed-window route inside the compact convex carrier.
\item $H$ records componentwise $\hsame$ transport for domain, affine ambient, family, commutation, fixed-window, invariant-subcarrier, replay, provenance, and local naming rows.
\item $R$ records displayed $\Cont$ replay from a family request through $D,A,F,C,W,I,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MarkovKakutaniFixedPointUp$, $\ConvexSetUp$, $\FunctionalAnalysisUp$, $\SchauderFixedPointUp$, $\KakutaniFixedPointUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MarkovKakutaniFixedPointUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,A,F,C,W,I,H,R,P,N$. It has no coordinate for an unbounded operator family, host compactness, selected fixed point, quotient equality of nets, or an ambient topological-vector-space theorem.
\end{definition}

\begin{theorem}[Markov-Kakutani fixed point obligation surface]\label{thm:markov-kakutani-fixed-point-obligation-surface}
For every accepted $\MarkovKakutaniFixedPointUp$ carrier
$$
M=(D,A,F,C,W,I,H,R,P,N),
$$
the local $\NameCert_{\MarkovKakutaniFixedPointUp}$ surface consists exactly of compact-convex domain admission through $D$, affine ambient admission through $A$, finite commuting-family admission through $F$, pairwise commutation exposure through $C$, fixed-window exposure through $W$, invariant-subcarrier handoff through $I$, componentwise $\hsame$ stability through $H$, displayed $\Cont$ replay through $R$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:markov-kakutani-fixed-point-carrier}. The compact-convex, affine, commuting-family, commutation, fixed-window, and invariant-subcarrier data are exactly the rows $D,A,F,C,W,I$.

The domain and affine rows bind the finite ambient context before any map in the family is read. The family row $F$ then lists only displayed affine self-maps, and the commutation ledger $C$ records pairwise commutation inside that finite list.

The fixed-window and invariant-subcarrier rows $W,I$ are the only route to a common fixed-point obligation. Finally $H,R,P,N$ transport, replay, source, and name the same packet. Since no additional coordinate is present, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Markov-Kakutani commuting handoff]\label{thm:markov-kakutani-fixed-point-commuting-handoff}
Every accepted consumer of a $\MarkovKakutaniFixedPointUp$ packet that asks for a common fixed-window read factors through
$$
\ConvexSetUp,\ \FunctionalAnalysisUp,\ \SchauderFixedPointUp,\ \KakutaniFixedPointUp
\longmapsto
D,A,F,C,W,I,H,R,P,N .
$$
The exported object is a finite commuting-family fixed-window packet. It is not a selected fixed point, a host compactness theorem, a global choice principle, a quotient of approximating nets, or an ambient locally convex-space completion.
\end{theorem}
\begin{proof}
Open the accepted carrier using \autoref{def:markov-kakutani-fixed-point-carrier}. A consumer must first read the compact convex domain row $D$ and the affine ambient row $A$, so the route is grounded in the displayed convex and functional-analysis siblings.

Next read the finite family row $F$ and the commutation ledger $C$. These rows expose only the listed affine self-maps and their pairwise commutation windows, so no unbounded operator family or host selection principle enters the packet.

The fixed-window row $W$ is then interpreted inside the invariant-subcarrier row $I$. The Schauder and Kakutani siblings provide fixed-point handoff surfaces for the displayed compact-convex route, but the Markov-Kakutani packet exports only the finite common-window ledger named by $W,I$.

Finally $H,R,P,N$ preserve the same carrier under transport, replay, provenance, and local naming. The exclusion clauses in the carrier therefore prevent selected fixed points, host compactness, quotient-net equality, and ambient completion from leaving the packet.
\end{proof}

\falsifiablePrediction{Every accepted $\MarkovKakutaniFixedPointUp$ consumer must expose compact-convex domain, affine ambient, finite commuting-family, pairwise commutation, fixed-window, invariant-subcarrier, hsame, Cont, Pkg, and NameCert rows before it can read a common fixed-window obligation.}

\independenceWitness{convexset, functionalanalysis, schauder-fixed-point, kakutani-fixed-point: $\MarkovKakutaniFixedPointUp$ is not bijective to any listed sibling because it jointly carries a finite commuting affine family, commutation ledger, fixed-window rows, invariant-subcarrier handoff, transport, replay, provenance, and local naming.}

\closureat{MarkovKakutaniFixedPointUp}{seedStr}

\begin{closurestatus}{\MarkovKakutaniFixedPointUp}
  \constructivestory{A $\MarkovKakutaniFixedPointUp$ packet is generated from compact-convex domain rows, affine ambient rows, finite commuting-family rows, pairwise commutation ledgers, fixed-window rows, invariant-subcarrier handoff rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:markov-kakutani-fixed-point-carrier}, \autoref{thm:markov-kakutani-fixed-point-obligation-surface}, and \autoref{thm:markov-kakutani-fixed-point-commuting-handoff} seed the finite Markov-Kakutani fixed-point packet over displayed compact-convex, affine, commuting-family, fixed-window, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host compactness, selected common fixed points, global choice, quotient equality of nets, ambient locally convex completion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-convex domain admission, affine-family routing, commutation ledger coverage, fixed-window exposure, invariant-subcarrier handoff, transport, replay, provenance, and local naming for BEDC.Derived.MarkovKakutaniFixedPointUp.}
\end{closurestatus}
