\begin{theorem}[HaltingDistinction root inscription trace totality]
\label{thm:halting-distinction-root-inscription-trace-totality}
Every root obligation read of an accepted $\HaltingDistinctionUp$ packet exposes the inscription-event route only through the finite rows
$$
Q,T,Z,H,C,P,N.
$$
The inscription event reads the diagonal row $Z$ with the sibling trace row $T$, componentwise transports $H$, displayed route $C$, package provenance $P$, and local ledger $N$; it does not expose a total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:halting-distinction-carrier}. The available rows are exactly $Q,T,Z,H,C,P,N$, with $Z$ serving as the diagonal inscription row and $T$ serving as the finite trace row.

Apply the inscription-event handoff and the inscription trace gate. They route the inscription read through $Z$ and the surrounding support rows while keeping the trace-normal-form sibling attached to $T$.

Finally use the consumer boundary package. Since the package is exhausted by the finite $\BHist$, $\Cont$, $\hsame$, $\Pkg$, and $\NameCert$ rows, no total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure can be read from the inscription route.
\end{proof}

\begin{theorem}[HaltingDistinction root diagonal inscription nonescape]
\label{thm:halting-distinction-root-diagonal-inscription-nonescape}
For an accepted $\HaltingDistinctionUp$ packet, the diagonal row $Z$ cannot escape the root obligation surface as a halting decision. Any diagonal-inscription consumer reaches $Z$ only along the displayed $Q,T,H,C,P,N$ support, and the trace-normal-form sibling reads the same finite $\Cont$ route rather than a host evaluation row.
\end{theorem}
\begin{proof}
Start with the diagonal boundary theorem and root ledger non-escape. They keep $Z$ inside the local packet and forbid reinterpreting the diagonal row as evaluator data.

Use trace readability and the trace-normal-form handoff for the sibling route. The normal-form consumer reads $T$ through the displayed continuation row $C$, with transports supplied by $H$ and provenance by $P,N$.

The inscription-event handoff then binds the diagonal read to the same finite packet. Thus neither the diagonal row nor its trace-normal-form sibling yields a total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{proof}

\begin{theorem}[HaltingDistinction root consumer obstruction exhaustion]
\label{thm:halting-distinction-root-consumer-obstruction-exhaustion}
Every obstruction-facing root consumer of an accepted $\HaltingDistinctionUp$ packet factors through the displayed carrier rows
$$
Q,T,Z,H,C,P,N
$$
and the obstruction handoff route. The consumer may inspect the certificate-history pair, finite trace, diagonal inscription row, componentwise transports, displayed continuation route, provenance, and local $\NameCert$ ledger, but it cannot add a total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{theorem}
\leanchecked{BEDC.Derived.HaltingDistinctionUp.HaltingDistinctionCarrier\_root\_consumer\_obstruction\_exhaustion}
\begin{proof}
Project the carrier rows and apply the route obstruction triad. This sends obstruction-facing consumption through the displayed packet and the $\HaltingObstructionUp$ sibling before any obstruction ledger is read.

Next apply the root inscription trace totality and root diagonal inscription nonescape theorems above. They bind the inscription and trace-normal-form sides to the same $Q,T,Z,H,C,P,N$ surface.

Finally use the consumer boundary package with consumer non-escape. Coordinate exhaustion leaves only the finite obstruction handoff rows, so the downstream consumer receives no total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{proof}

\begin{theorem}[HaltingDistinction observation boundary]
\label{thm:halting-distinction-observation-boundary}
Every observation-facing consumer of an accepted $\HaltingDistinctionUp$ carrier must read the certificate-history pair, finite trace row, diagonal row, inscription-event row, trace-normal-form route, obstruction ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows before any obstruction conclusion is exposed. The read is bounded by the finite BEDC rows
$$
Q,T,Z,H,C,P,N
$$
and by the sibling surfaces of $\HaltingDistinctionTraceUp$, $\InscriptionEventUp$, $\ContinuationTraceNormalFormUp$, and $\HaltingObstructionUp$. It does not expose a total halting predicate, host evaluator, divergence oracle, global truth classifier, or unbounded execution semantics.
\end{theorem}
\begin{proof}
First apply \autoref{thm:halting-distinction-root-inscription-trace-totality}. It sends observation of the inscription event through the finite diagonal row $Z$, trace row $T$, transports $H$, route row $C$, provenance row $P$, and local ledger $N$.

Next apply \autoref{thm:halting-distinction-root-diagonal-inscription-nonescape}. This keeps the diagonal inscription and trace-normal-form route inside the same finite continuation surface, so the consumer cannot reinterpret the read as host evaluation data.

Finally apply \autoref{thm:halting-distinction-root-consumer-obstruction-exhaustion} together with the sibling trace, inscription-event, trace-normal-form, and obstruction surfaces named in \autoref{ch:concrete-instances-haltingdistinction-namecert}. The obstruction-facing conclusion is therefore available only after the displayed certificate-history, trace, diagonal, inscription, normal-form, obstruction, transport, continuation, package, and naming rows have been read, and no total halting predicate, divergence oracle, global truth classifier, host evaluator, or unbounded execution semantics is introduced.
\end{proof}
