\begin{theorem}[HaltingDistinction root consumer obstruction exhaustion]
\label{thm:halting-distinction-root-consumer-obstruction-exhaustion}
Every obstruction-facing root consumer of an accepted $\HaltingDistinctionUp$ packet factors through the displayed carrier rows
$$
Q,T,Z,H,C,P,N
$$
and the obstruction handoff route. The consumer may inspect the certificate-history pair, finite trace, diagonal inscription row, componentwise transports, displayed continuation route, provenance, and local $\NameCert$ ledger, but it cannot add a total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{theorem}
\leanchecked{BEDC.Derived.HaltingDistinctionUp.HaltingDistinctionCarrier\_root\_consumer\_obstruction\_exhaustion}
\begin{proof}
Project the carrier rows and apply the route obstruction triad. This sends obstruction-facing consumption through the displayed packet and the $\HaltingObstructionUp$ sibling before any obstruction ledger is read.

Next apply the root inscription trace totality and root diagonal inscription nonescape theorems above. They bind the inscription and trace-normal-form sides to the same $Q,T,Z,H,C,P,N$ surface.

Finally use the consumer boundary package with consumer non-escape. Coordinate exhaustion leaves only the finite obstruction handoff rows, so the downstream consumer receives no total halting predicate, global truth predicate, host evaluator, divergence oracle, or hidden decision procedure.
\end{proof}
