\begin{theorem}[Cauchy witness ledger budget Real route totality]
\label{thm:cauchy-witness-ledger-budget-real-route-totality}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Every budget read, $\StreamNameUp$ window read, $\RegSeqRatUp$ readback, and $\RealUp$ completion-facing read of $L$ routes through the finite rows $Q,B,S,K,H,C,P,N$. The route is the displayed diagonal-budget, observation-budget, synchronizer, and completion-seal path, with no completion choice, quotient representative, host limit, detached rational readback, or second stream source.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_budget\_real\_route\_totality}
\begin{proof}
Apply \autoref{thm:cauchy-witness-ledger-budget-factorization}. It orders the budget-facing route through $Q \longmapsto B \longmapsto S \longmapsto K$, while the carrier and NameCert rows supply only $H,C,P,N$ as structural coordinates.

Use \autoref{thm:cauchy-witness-ledger-streamname-window-source-lock}, \autoref{thm:cauchy-witness-ledger-regseqrat-readback-totality}, and \autoref{thm:cauchy-witness-ledger-real-seal-refusal-boundary}. These rows identify the StreamName source, the RegSeqRat readback, and the off-route Real refusal boundary with the same finite ledger. Hence every admitted read is exhausted by $Q,B,S,K,H,C,P,N$.
\end{proof}

\begin{theorem}[Cauchy witness ledger StreamName RegSeq factorization]
\label{thm:cauchy-witness-ledger-streamname-regseq-factorization}
For an accepted $\CauchyWitnessLedgerUp$ packet $L=(Q,B,S,K,H,C,P,N)$, the $\StreamNameUp$ window source and every $\RegSeqRatUp$ readback factor through the same $Q \longmapsto B$ budget source before $S$ or $K$ is public. Componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row preserve this source without adding a tail oracle, detached dyadic completion, or host Real limit.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_streamname\_regseq\_factorization}
\begin{proof}
Read \autoref{thm:cauchy-witness-ledger-streamname-window-source-lock}. The stream window is fixed by the diagonal-budget and observation-budget rows, then transported through $H,C,P,N$.

Now apply \autoref{thm:cauchy-witness-ledger-regseqrat-readback-totality}. The regular-rational readback is supplied by the same finite $\StreamNameUp$ and $\DyadicRatCoreUp$ route already displayed by $Q$ and $B$. The synchronizer-classifier lock keeps $S$ and $K$ attached to that source, so no independent rational or Real-completion coordinate is introduced.
\end{proof}

\begin{theorem}[Cauchy witness ledger Real completion nonescape]
\label{thm:cauchy-witness-ledger-real-completion-nonescape}
Let $L=(Q,B,S,K,H,C,P,N)$ be accepted. Any $\RealUp$ completion read admitted by $L$ reaches the classifier row $K$ only through the finite route $Q \longmapsto B \longmapsto S \longmapsto K$ and the structural rows $H,C,P,N$. Reads outside that route fall under the Real seal refusal boundary and export no selected limit, quotient stream, host equality, countable-choice row, ambient completeness theorem, hidden tail oracle, or alternate seal.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-witness-ledger-real-completion-handoff} and \autoref{thm:cauchy-witness-ledger-root-seal-readback}. They place every completion-facing read behind the diagonal budget, observation budget, synchronizer, and completion-seal classifier.

Finally use \autoref{thm:cauchy-witness-ledger-real-seal-refusal-boundary}. A request outside the displayed route has no carrier coordinate in $\BHist$, no accepted $\hsame$ or $\Cont$ replay, and no $\Pkg$ or $\NameCert$ witness. Thus the read remains finite and cannot escape to an external completion principle.
\end{proof}

\begin{theorem}[Cauchy witness ledger root budget row totality]\label{thm:cauchy-witness-ledger-root-budget-row-totality}
Every accepted root read of $L=(Q,B,S,K,H,C,P,N)$ exposes the diagonal-budget row $Q$ and the observation-budget row $B$ before any completion-seal classifier read is public.
\end{theorem}
\begin{proof}
Use \autoref{def:cauchy-witness-ledger-carrier}, \autoref{thm:cauchy-witness-ledger-budget-factorization}, and \autoref{thm:cauchy-witness-ledger-readback-totality}. The carrier has $Q$ and $B$ as displayed analytic rows, the budget factorization orders them before $S$ and $K$, and readback totality gives no root read outside $Q,B,S,K,H,C,P,N$.
\end{proof}

\begin{theorem}[Cauchy witness ledger root seal route totality]\label{thm:cauchy-witness-ledger-root-seal-route-totality}
Every root seal read of an accepted $\CauchyWitnessLedgerUp$ packet passes through the finite route $Q \longmapsto B \longmapsto S \longmapsto K$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchy-witness-ledger-root-seal-readback} and \autoref{thm:cauchy-witness-ledger-synchronizer-classifier-lock}. The first theorem places seal readback behind the displayed route, and the second keeps $K$ attached to the same $Q \longmapsto B \longmapsto S$ source.
\end{proof}

\begin{theorem}[Cauchy witness ledger root NameCert threshold]\label{thm:cauchy-witness-ledger-root-namecert-threshold}
The root rows $Q,B,S,K$ together with $H,C,P,N$ form the $\NameCert_{\CauchyWitnessLedgerUp}$ threshold surface for the witness ledger.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_root\_namecert\_threshold}
\begin{proof}
Read \autoref{thm:cauchy-witness-ledger-namecert-obligations}, \autoref{thm:cauchy-witness-ledger-budget-factorization}, and \autoref{thm:cauchy-witness-ledger-synchronizer-classifier-lock}. These statements supply the displayed obligation rows, order the budget route, and bind the synchronizer-classifier threshold without adding any row outside $Q,B,S,K,H,C,P,N$.
\end{proof}

\begin{theorem}[Cauchy witness ledger formal target surface]
\label{thm:cauchy-witness-ledger-formal-target-surface}
For an accepted $\CauchyWitnessLedgerUp$ packet $L=(Q,B,S,K,H,C,P,N)$, the encoded target \texttt{BEDC.Derived.CauchyWitnessLedgerUp.taste\_gate} is the formal target surface for the finite route $Q,B,S,K,H,C,P,N$. Any future scaffold checking of that target must preserve the diagonal-budget row, observation-budget row, synchronizer row, completion-seal classifier row, componentwise transport rows, displayed replay rows, provenance row, and local $\NameCert$ row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_formal\_target\_surface}
\begin{proof}
The root budget threshold is \autoref{thm:cauchy-witness-ledger-root-budget-row-totality}. It forces the diagonal-budget row $Q$ and observation-budget row $B$ to be public before the completion-seal classifier is read.

The root seal threshold is \autoref{thm:cauchy-witness-ledger-root-seal-route-totality}. It confines the seal route to $Q \longmapsto B \longmapsto S \longmapsto K$.

The local naming threshold is \autoref{thm:cauchy-witness-ledger-root-namecert-threshold}. Together with \autoref{thm:cauchy-witness-ledger-real-completion-nonescape}, it keeps completion-facing reads inside the same finite route and excludes selected limits, quotient streams, host equality, countable choice, ambient completeness, hidden tails, and alternate seals. Thus the named Lean target is exactly the finite formal surface whose later checking must preserve those rows.
\end{proof}

\begin{theorem}[Cauchy witness ledger four-face Real completion lock]
\label{thm:cauchy-witness-ledger-four-face-real-completion-lock}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Its formal target surface factors through exactly the four Phase Real and Completion faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, together with only the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Thus every roadmap-exit consumer of the ledger reads the same four-face route and no route adds quotient streams, selected limits, host sequence equality, ambient Real completeness, metric-completeness data, countable choice, or standard bridge rows.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-witness-ledger-formal-target-surface}. It identifies the accepted formal surface with the finite route $Q,B,S,K,H,C,P,N$, so a consumer can expose only the budget, window, readback, Real-seal classifier, and structural rows already carried by $L$.

Next apply \autoref{thm:streamname-real-completion-four-object-exit-route} and \autoref{thm:streamname-real-completion-four-object-exit-consumer-exhaustion}. These force the Real-completion exit route through the four displayed faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, and exhaust every consumer read at that boundary.

Finally use \autoref{thm:streamname-cauchy-witness-ledger-exit-saturation}. It attaches the Cauchy witness ledger to that same four-object exit packet through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Since neither the ledger surface nor the exit packet carries quotient streams, selected limits, host sequence equality, ambient Real completeness, metric-completeness data, countable choice, or standard bridge rows, no second completion-facing route remains.
\end{proof}

\begin{theorem}[Cauchy witness ledger budget-selector four-face exhaustion]
\label{thm:cauchy-witness-ledger-budget-selector-four-face-exhaustion}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet, and let $F=(B_0,S_0,W,D,R,E,H_0,C_0,P_0,N_0)$ be an accepted $\FiniteObservationBudgetSelectorUp$ packet whose selected finite windows $W$ are the same $\StreamNameUp$ window face consumed by $L$. Then every Phase Real and Completion consumer of $L$ factors through the selector route of $F$ and the same terminal four-face packet
$$
\FiniteObservationBudgetSelectorUp,\quad \StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
together with only the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Thus passing through the observation-budget selector preserves the terminal route already locked by $L$: the consumer receives the selected window face, the dyadic ledger face, the regular-rational readback face, and the Real seal face, but no quotient stream, selected limit, host sequence equality, ambient Real completeness, metric-completeness datum, countable-choice row, or standard bridge row.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-witness-ledger-four-face-real-completion-lock}. It places every roadmap-exit consumer of $L$ on the four Phase Real and Completion faces $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, with only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Move to the selector packet. By \autoref{thm:finite-observation-budget-selector-budget-route-determinacy}, the accepted packet $F$ determines one finite route from its budget row through the selected schedule, window family, dyadic ledger, regular readback, and seal. By \autoref{thm:finite-observation-budget-selector-dyadic-window-exhaustion}, every dyadic observation exported by $D$ is already read from the selected finite windows $W$.

Use the shared-window hypothesis to identify $W$ with the $\StreamNameUp$ window face consumed by $L$. The selector therefore supplies exactly the same window and dyadic-ledger coordinates that the ledger route exposes before the $\RegSeqRatUp$ readback and $\RealUp$ seal are public.

Finally apply \autoref{thm:streamname-open-phase-four-face-terminality}. Once the shared window, dyadic ledger, readback, seal, and displayed support rows agree, the Phase Real and Completion consumer has no second terminal route. Since neither the selector route nor the ledger route carries quotient streams, selected limits, host sequence equality, ambient Real completeness, metric-completeness data, countable choice, or standard bridge rows, passing through $\FiniteObservationBudgetSelectorUp$ preserves the same terminal four-face packet.
\end{proof}

\begin{theorem}[Cauchy witness ledger open-phase budget route handoff]
\label{thm:cauchy-witness-ledger-open-phase-budget-route-handoff}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Suppose its displayed rows include the budget selector route, the completion-seal route, the $\StreamNameUp$--$\RegSeqRatUp$ factorization, and the $\RealUp$ completion nonescape boundary. Then $L$ determines one Real-and-completion handoff surface through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, supported only by the finite rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Every open-phase consumer reading the packet therefore receives the same dyadic budget, named stream window, regular-rational readback, and Real seal coordinates. No off-packet completion coordinate, quotient stream, selected limit, host sequence equality, ambient Real completeness theorem, metric-completeness datum, countable-choice row, or standard bridge row is exported by the handoff.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-witness-ledger-budget-real-route-totality} and \autoref{thm:cauchy-witness-ledger-root-seal-route-totality}. These rows place the budget reads and the completion-seal reads on the finite route $Q \longmapsto B \longmapsto S \longmapsto K$, with $H,C,P,N$ as the only structural support.

Next use \autoref{thm:cauchy-witness-ledger-streamname-regseq-factorization} and \autoref{thm:cauchy-witness-ledger-real-completion-nonescape}. The named stream source and the regular-rational readback both factor through the same budget source, while every completion-facing read remains inside the displayed Real seal boundary.

Apply \autoref{thm:cauchy-witness-ledger-four-face-real-completion-lock} and \autoref{thm:cauchy-witness-ledger-budget-selector-four-face-exhaustion}. They identify the terminal consumer surface with the four open Phase Real and Completion faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, even when the observation-budget selector mediates the selected windows.

Thus a downstream consumer can only replay the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route already carried by $L$. Since each cited row is exhausted by that route, no coordinate remains from which an external completion object or second Real handoff could be read.
\end{proof}

\begin{theorem}[Cauchy witness ledger selector-seal terminality]
\label{thm:cauchy-witness-ledger-selector-seal-terminality}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Let $T=(B_0,W,R,L_0,E,H_0,C_0,P_0,N_0)$ be an accepted $\RealCompletionSelectorSealUp$ packet whose selected window row $W$, $\RegSeqRatUp$ readback row $R$, and $\CauchyLimitSealUp$ row $L_0$ agree with the ledger route exposed by $L$ through the observation-budget selector.

Then every Phase Real and Completion consumer of $L$ factors through the unique terminal route
$$
\CauchyWitnessLedgerUp \longmapsto \FiniteObservationBudgetSelectorUp \longmapsto \RealCompletionSelectorSealUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \CauchyLimitSealUp \longmapsto \RealUp
$$
with only the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. No quotient stream, selected limit, host equality, ambient completeness, countable-choice row, second completion route, or standard bridge row remains after this factorization.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-witness-ledger-open-phase-budget-route-handoff}. It places every open-phase consumer of $L$ on the finite Real-and-completion handoff surface through the displayed budget, named stream window, regular-rational readback, and Real seal rows, with only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Next apply \autoref{thm:cauchy-witness-ledger-budget-selector-four-face-exhaustion}. The observation-budget selector transports the same selected window and readback information without adding quotient streams, selected limits, host sequence equality, ambient Real completeness, metric-completeness data, countable choice, or standard bridge rows.

Use the agreement hypotheses for $T$. The selected window $W$, readback row $R$, and limit row $L_0$ are the same rows already consumed by the ledger route, so the selector-seal packet is attached to the handoff rather than forming a second completion source.

Finally use \autoref{thm:real-completion-selector-seal-route-determinacy} and \autoref{thm:real-completion-selector-seal-nonescape}. Determinacy gives a single finite selector-seal route, and non-escape exhausts every completion consumer at $B_0,W,R,L_0,E,H_0,C_0,P_0,N_0$. Hence the only remaining route is the displayed terminal chain from $\CauchyWitnessLedgerUp$ to $\RealUp$ through the selector and seal packets.
\end{proof}

\begin{theorem}[Cauchy witness ledger selector agreement terminal collapse]
\label{thm:cauchy-witness-ledger-selector-agreement-terminal-collapse}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Let $F=(B_0,S_0,W,D,R_F,E_F,H_F,C_F,P_F,N_F)$ be an accepted $\FiniteObservationBudgetSelectorUp$ packet, and let $T=(B_1,W_1,R_T,L_1,E_T,H_T,C_T,P_T,N_T)$ be an accepted $\RealCompletionSelectorSealUp$ packet. Suppose the three packets agree on the selected window, the $\RegSeqRatUp$ readback, the $\CauchyLimitSealUp$ row, and the $\RealUp$ seal row exposed by the ledger route.

Then every $\RealAlgOrderUp$, $\MetricSpaceUp$, or $\SOneUp$ consumer of the Real-and-completion surface factors through the single terminal chain
$$
\CauchyWitnessLedgerUp \longmapsto \FiniteObservationBudgetSelectorUp \longmapsto \RealCompletionSelectorSealUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \CauchyLimitSealUp \longmapsto \RealUp.
$$
The consumer receives only the displayed selected-window route, regular-rational readback, limit-seal row, Real seal row, and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It cannot introduce quotient streams, selected limits, host equality, ambient completeness, countable choice, a second completion route, or any separate RealAlgOrder, MetricSpace, or $\SOneUp$ completion source.
\end{theorem}
\begin{proof}
First attach the ledger to the selector-seal route. By \autoref{thm:cauchy-witness-ledger-selector-seal-terminality}, the accepted ledger packet and selector-seal packet already force every Phase Real and Completion consumer through the displayed route from $\CauchyWitnessLedgerUp$ to $\RealUp$.

Next identify the four open faces. Apply \autoref{thm:streamname-open-phase-four-face-terminality} to the agreed selected window, dyadic observation window, regular readback, and Real seal rows, and then apply \autoref{thm:real-l10-four-face-audit-clean-handoff}. These rows are consumed as one terminal four-face packet rather than as independent completion coordinates.

Now read the downstream positive-boundary consumers. The RealAlgOrder, MetricSpace, and $\SOneUp$ consumer theorems use the same positive Real boundary: they read the Real row after the StreamName, RegSeqRat, CauchyLimitSeal, and Real seal faces have already been fixed. Since the hypotheses identify those faces across $L$, $F$, and $T$, no consumer in this family has another source from which a completion route could be read.

Finally use nonescape for the selector-seal and ledger routes. The selector-seal packet exports no quotient stream, selected limit, host equality, ambient completeness, countable choice, or second completion route, and the ledger route exports no off-packet Real completion data. Thus the only available route for the three consumer families is the displayed terminal chain.
\end{proof}

\begin{corollary}[Cauchy witness ledger budget Real route strict local obstruction]
\label{cor:cauchy-witness-ledger-budget-real-route-strict-local-obstruction}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Any displayed failure, refusal, separation, or countermodel row attached to the budget Real route of $L$ is a strict local obstruction: it blocks only the proposed converse read, detached reuse, or off-route completion request that tries to bypass
$$
Q \longmapsto B \longmapsto S \longmapsto K
$$
and the structural rows $H,C,P,N$. Every consumer-facing use that remains admitted factors through the diagonal-budget row, observation-budget row, synchronizer row, completion-seal classifier row, componentwise transport row, displayed replay row, provenance row, and local $\NameCert$ row. A request using any unlisted coordinate is refused at the Real seal boundary and exports no selected limit, quotient stream, host equality, countable-choice row, ambient completeness theorem, hidden tail oracle, alternate seal, or external validation witness.

Consequently the obstruction cannot be reinterpreted as a global impossibility theorem for $\RealUp$ completion-facing reads, as a host theorem about Real completeness, or as hidden validation by an external completion principle. It is only the local refusal of the named converse or reuse route outside the displayed ledger packet.
\end{corollary}
\begin{proof}
Start with \autoref{thm:cauchy-witness-ledger-budget-real-route-totality}. It says that every budget read, $\StreamNameUp$ window read, $\RegSeqRatUp$ readback, and $\RealUp$ completion-facing read admitted by $L$ routes through exactly the finite rows $Q,B,S,K,H,C,P,N$. The same statement names the diagonal-budget, observation-budget, synchronizer, and completion-seal path as the whole admitted route and excludes completion choice, quotient representatives, host limits, detached rational readbacks, and second stream sources from that path.

Now apply \autoref{thm:cauchy-witness-ledger-real-completion-nonescape}. A completion read reaches $K$ only through $Q \longmapsto B \longmapsto S \longmapsto K$ together with $H,C,P,N$. If a displayed failure, refusal, separation, or countermodel row is triggered, it is triggered by a request outside that finite route; the nonescape theorem sends such a request to the Real seal refusal boundary and gives it no selected limit, quotient stream, host equality, countable-choice row, ambient completeness theorem, hidden tail oracle, or alternate seal.

Thus the consumer-facing alternatives split sharply. An admitted consumer factors through the displayed ledger rows by totality. A non-admitted consumer is rejected as an unlisted coordinate by nonescape. The refusal branch therefore has no carrier coordinate from which to state a global impossibility result, no host Real object from which to derive an ambient theorem, and no exported external witness from which hidden validation could be read. The only blocked object is the named converse or reuse request that attempted to leave the finite ledger route.
\end{proof}
