\begin{theorem}[Cauchy witness ledger root diagnostic budget totality]
\label{thm:cauchy-witness-ledger-root-diagnostic-budget-totality}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet. Every root diagnostic read of $L$ consumes the diagonal-budget row $Q$, observation-budget row $B$, seal-synchronizer row $S$, completion-seal classifier row $K$, componentwise transport row $H$, displayed continuation row $C$, provenance row $P$, and local NameCert row $N$. No such root read can bypass the diagonal budget, observation budget, synchronizer, or completion-seal classifier.
\end{theorem}
\begin{proof}
Begin with \autoref{def:cauchy-witness-ledger-carrier}. The carrier exposes only $Q,B,S,K,H,C,P,N$, so any root diagnostic read must land on the displayed ledger rows.

Apply \autoref{thm:cauchy-witness-ledger-namecert-obligations}. The local NameCert surface requires carrier admission, budget exposure, synchronizer exposure, classifier exposure, transport, replay, provenance, and local naming for the same finite packet.

Now use \autoref{thm:cauchy-witness-ledger-budget-factorization}. It orders the analytic budget route through $Q$, then $B$, then $S$, then $K$. Since the root diagnostic read is a read of the accepted packet, it cannot omit any one of those budget rows while still preserving the displayed NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_root\_diagnostic\_budget\_totality}

\begin{theorem}[Cauchy witness ledger root seal classifier lock]
\label{thm:cauchy-witness-ledger-root-seal-classifier-lock}
For an accepted $\CauchyWitnessLedgerUp$ packet $L=(Q,B,S,K,H,C,P,N)$, the completion-seal classifier row $K$ is exposed only after the route
$$
Q \longmapsto B \longmapsto S
$$
has been displayed. A consumer cannot read $K$ as a detached classifier row before the diagonal-budget row, observation-budget row, and seal-synchronizer row have been consumed.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_root\_seal\_classifier\_lock}
\begin{proof}
First read the carrier in \autoref{def:cauchy-witness-ledger-carrier}. The row $K$ is one coordinate of the same finite packet as $Q,B,S,H,C,P,N$, not a separate classifier object.

Apply \autoref{thm:cauchy-witness-ledger-namecert-obligations} to bind $K$ to the local certificate for the packet. The certificate exposes $K$ together with the displayed budget and synchronizer rows.

Finally use \autoref{thm:cauchy-witness-ledger-budget-factorization}. The factorization places the classifier after $Q \longmapsto B \longmapsto S$, so a detached read of $K$ would skip part of the certified route and would not be a root read of the accepted packet.
\end{proof}

\begin{theorem}[Cauchy witness ledger root budget classifier determinacy]
\label{thm:cauchy-witness-ledger-root-budget-classifier-determinacy}
Let $L=(Q,B,S,K,H,C,P,N)$ and $L'=(Q',B',S',K',H',C',P',N')$ be accepted $\CauchyWitnessLedgerUp$ packets. Suppose their public root reads agree on the displayed budget route
$$
Q \longmapsto B \longmapsto S
$$
and on the structural rows $H,C,P,N$. Then the completion-seal classifier read is determined on that public route: $K$ and $K'$ name the same route-bound classifier read. In particular, no second completion-seal classifier for the same public root route can be attached to a different stream source, $\RegSeqRat$ source, $\DyadicRatCore$ source, $\RealUp$ source, tail source, limit source, or seal source.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchy-witness-ledger-root-diagnostic-budget-totality} for both packets. Every public root diagnostic read exposes exactly the diagonal-budget row, observation-budget row, seal-synchronizer row, completion-seal classifier row, componentwise transport row, displayed continuation row, provenance row, and local NameCert row.

The assumed agreement on $Q \longmapsto B \longmapsto S$ and on $H,C,P,N$ therefore identifies the public route on which the classifier row is read. Apply \autoref{thm:cauchy-witness-ledger-root-seal-classifier-lock}: $K$ is available only after that displayed route and cannot be read as a detached classifier before the budget and synchronizer rows have been consumed.

It remains to exclude an off-route classifier with a different completion source. Apply \autoref{thm:cauchy-witness-ledger-root-forbidden-coordinate-exclusion-packet} and \autoref{thm:cauchy-witness-ledger-root-terminal-route-exhaustion}. Since the root packet has no quotient stream equality, host real equality, selected external limit, countable-choice row, ambient completeness coordinate, or detached classifier, every terminal completion-facing read is exhausted by the same finite ledger surface. Thus any classifier attached to the agreed public route is the route-bound classifier read already named by $K$ and $K'$.
\end{proof}

\begin{theorem}[Cauchy witness ledger root forbidden coordinate exclusion packet]
\label{thm:cauchy-witness-ledger-root-forbidden-coordinate-exclusion-packet}
The root packet of an accepted $\CauchyWitnessLedgerUp$ carrier $L=(Q,B,S,K,H,C,P,N)$ contains no quotient stream equality, host real equality, selected external limit, countable-choice row, or ambient completeness coordinate. All root completion-facing reads are confined to the displayed budget route, structural rows, provenance row, and local NameCert row.
\end{theorem}
\begin{proof}
Start from \autoref{def:cauchy-witness-ledger-carrier}. Its root coordinates are exactly $Q,B,S,K,H,C,P,N$, and none of these is a quotient stream equality, host real equality, selected external limit, countable-choice row, or ambient completeness coordinate.

Use \autoref{thm:cauchy-witness-ledger-budget-factorization} to locate every completion-facing read on the budget route through $Q,B,S,K$. The structural rows $H,C,P,N$ preserve and name that route rather than adding a separate completion source.

Finish with \autoref{thm:cauchy-witness-ledger-forbidden-coordinate-exclusion}. That theorem rules out the forbidden coordinates for the ledger surface, and the present root packet exposes no additional row on which such a coordinate could be introduced.
\end{proof}

\begin{theorem}[Cauchy witness ledger root terminal route exhaustion]
\label{thm:cauchy-witness-ledger-root-terminal-route-exhaustion}
Every terminal root diagnostic or completion-facing read of an accepted $\CauchyWitnessLedgerUp$ packet $L=(Q,B,S,K,H,C,P,N)$ is exhausted by the displayed route $Q,B,S,K,H,C,P,N$. The classifier row $K$ is available only after the route
$$
Q \longmapsto B \longmapsto S
$$
has been displayed, and the structural rows $H,C,P,N$ transport, replay, package, and name that same route.

No terminal read exports quotient stream equality, host real equality, a selected external limit, a countable-choice row, an ambient completeness coordinate, or a detached classifier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchy-witness-ledger-root-diagnostic-budget-totality}. It places every root diagnostic read on the packet rows $Q,B,S,K,H,C,P,N$, with the budget and synchronizer rows present before the terminal read can complete.

Next use \autoref{thm:cauchy-witness-ledger-root-seal-classifier-lock}. The classifier $K$ is not a detached object: it is read only after $Q \longmapsto B \longmapsto S$ and remains tied to the same local packet.

Finally apply \autoref{thm:cauchy-witness-ledger-root-forbidden-coordinate-exclusion-packet}. Since quotient stream equality, host real equality, selected external limits, countable choice, ambient completeness, and detached classifiers are not root coordinates, the terminal route is exactly the displayed finite ledger surface.
\end{proof}

\begin{theorem}[Cauchy witness ledger root diagnostic budget transport]
\label{thm:cauchy-witness-ledger-root-diagnostic-budget-transport}
Let $L=(Q,B,S,K,H,C,P,N)$ and $L'=(Q',B',S',K',H',C',P',N')$ be accepted $\CauchyWitnessLedgerUp$ packets. Suppose the displayed budget route
$$
Q \longmapsto B \longmapsto S \longmapsto K
$$
is transported componentwise through the displayed $H,H'$ rows and through the displayed continuation rows $C,C'$, with the history comparison governed by the stated $hsame$ rows and the continuation comparison governed by the stated $\Cont$ rows. Then root diagnostic reads and completion-facing terminal reads are stable along that transport: the transported route reads the same root budget, synchronizer, route-bound classifier, structural transport, continuation, provenance, and local NameCert rows.

Moreover, this transport does not introduce quotient stream equality, host real equality, a selected external limit, a countable-choice row, an ambient completeness coordinate, or a detached classifier.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchy-witness-ledger-root-diagnostic-budget-totality} to both accepted packets. The only rows visible to a root diagnostic read are the finite packet rows $Q,B,S,K,H,C,P,N$ and $Q',B',S',K',H',C',P',N'$.

Use \autoref{thm:cauchy-witness-ledger-root-seal-classifier-lock} to read the order of the route. The classifier rows $K$ and $K'$ are available only after their displayed routes through $Q \longmapsto B \longmapsto S$ and $Q' \longmapsto B' \longmapsto S'$, so componentwise transport cannot detach the classifier from the budget and synchronizer rows.

Now apply \autoref{thm:cauchy-witness-ledger-root-budget-classifier-determinacy}. Since the transport is through the displayed $H,H'$ and $C,C'$ rows, with the comparison confined to the stated $hsame$ and $\Cont$ rows, the classifier read on the transported public route is the route-bound read already named by $K$ and $K'$.

It remains to identify the terminal surface. Apply \autoref{thm:cauchy-witness-ledger-root-forbidden-coordinate-exclusion-packet} and \autoref{thm:cauchy-witness-ledger-root-terminal-route-exhaustion}. The terminal completion-facing read is exhausted by the same finite ledger surface, and none of the forbidden coordinates can be supplied by transport through $H,H'$ or $C,C'$.
\end{proof}
\leanchecked{BEDC.Derived.CauchyWitnessLedgerUp.CauchyWitnessLedgerCarrier\_root\_diagnostic\_budget\_transport}

\begin{corollary}[Cauchy witness ledger root diagnostic budget use determinacy]
\label{cor:cauchy-witness-ledger-root-diagnostic-budget-use-determinacy}
Let $L=(Q,B,S,K,H,C,P,N)$ be an accepted $\CauchyWitnessLedgerUp$ packet, and let $t$ be an accepted consumer-facing root diagnostic budget use of $L$. Once the displayed rows $Q,B,S,H,C,P,N$ are fixed, the use $t$ has only one accepted landing: it factors through the finite route
$$
Q \longmapsto B \longmapsto S \longmapsto K
$$
with route replay supplied by $C$, componentwise transport supplied by $H$, provenance supplied by $P$, and local naming supplied by $N$. Hence any other accepted consumer presentation over the same fixed rows chooses the same route-bound completion-seal classifier $K$, the same replay normal form through $C$, and the same exactness/readback decision named by the chapter. No alternate hidden coordinate, detached tail, selected external limit, duplicate classifier source, quotient stream equality, host real equality, countable-choice row, or ambient completeness coordinate can be used to produce a second accepted diagnostic budget use.
\end{corollary}
\begin{proof}
Apply \autoref{thm:cauchy-witness-ledger-root-diagnostic-budget-totality} to the accepted use $t$. Every root diagnostic read of $L$ consumes exactly the diagonal-budget row $Q$, observation-budget row $B$, seal-synchronizer row $S$, completion-seal classifier row $K$, componentwise transport row $H$, displayed continuation row $C$, provenance row $P$, and local NameCert row $N$. In particular, after $Q,B,S,H,C,P,N$ are fixed, the only remaining classifier-facing row visible to $t$ is the route-bound row $K$.

Now compare $t$ with any second accepted consumer presentation over the same fixed local rows. The hypotheses give agreement on the displayed budget route
$$
Q \longmapsto B \longmapsto S
$$
and on the structural rows $H,C,P,N$. By \autoref{thm:cauchy-witness-ledger-root-budget-classifier-determinacy}, the completion-seal classifier read is determined on that public route: the second presentation cannot attach a different stream source, $\RegSeqRat$ source, $\DyadicRatCore$ source, $\RealUp$ source, tail source, limit source, or seal source to the same diagnostic budget use.

The replay and exactness components are also fixed. By \autoref{thm:cauchy-witness-ledger-route-replay-exactness}, the displayed $\Cont$ row $C$ replays the route through $Q \longmapsto B \longmapsto S \longmapsto K$ before any $\RealUp$-facing read is admitted. By \autoref{thm:cauchy-witness-ledger-completion-classifier-readback}, the classifier readback for $K$ is public exactly through that displayed route with $H,C,P,N$. Thus an accepted presentation over the fixed rows has the same replay normal form and the same exactness/readback decision.

Finally use \autoref{thm:cauchy-witness-ledger-root-terminal-route-exhaustion} together with \autoref{thm:cauchy-witness-ledger-root-forbidden-coordinate-exclusion-packet}. The terminal diagnostic surface is exhausted by the displayed finite ledger rows, and the forbidden external coordinates are not root coordinates. Therefore no hidden coordinate or duplicate classifier source remains from which a second accepted use of $t$ could be produced.
\end{proof}
