\chapter{A Concrete Naming Certificate for $\SpectrahedronUp$}
\label{ch:concrete-instances-spectrahedron-namecert}
\origin{human}

Following Boyd--Vandenberghe convex optimization, the $\SpectrahedronUp$ packet records the finite BEDC surface by which an affine section of the semidefinite cone is presented as a convex feasible region. It sits after the matrix carrier of \autoref{ch:concrete-instances-matrix-namecert}, the linear-map row of \autoref{ch:concrete-instances-linearmap-namecert}, the vector-space boundary of \autoref{ch:concrete-instances-vecspace-namecert}, the semidefinite-cone packet of \autoref{ch:concrete-instances-semidefinitecone-namecert}, and the convex-set provenance of \autoref{ch:concrete-instances-convexset-namecert}. The chapter names the affine pencil route; it does not import host spectral calculus, determinant inequalities, quotient equality of matrices, selected feasible points, or ambient analytic closure.

\begin{definition}[Spectrahedron carrier]
\label{def:spectrahedron-carrier}
A $\SpectrahedronUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,L,A,S,K,V,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the affine-parameter row over the displayed $\VecSpaceUp$ source.
\item $L$ is the $\LinearMapUp$ row carrying the affine pencil direction from parameter rows to symmetric $\MatrixUp$ rows.
\item $A$ is the affine offset matrix row read through $\MatrixUp$.
\item $S$ is the symmetric matrix-pencil row naming the displayed sum $A+L(x)$ for each accepted parameter row.
\item $K$ is the $\SemidefiniteConeUp$ membership row for the displayed pencil matrix.
\item $V$ is the $\ConvexSetUp$ provenance row that records the accepted parameter rows as a convex feasible subset.
\item $T$ records componentwise $\hsame$ transport for parameter, linear-map, matrix, cone-membership, convex-provenance, replay, package, and local naming rows.
\item $C$ records displayed $\Cont$ replay from parameter reads through the affine pencil, semidefinite-cone membership, and convex-set provenance rows.
\item $P$ is the $\Pkg$ provenance over $\SpectrahedronUp$, $\MatrixUp$, $\SemidefiniteConeUp$, $\ConvexSetUp$, $\LinearMapUp$, $\VecSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SpectrahedronUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,L,A,S,K,V,T,C,P,N$. It has no coordinate for eigenvalue decompositions, determinant tests, quotient equality of matrix pencils, selected feasible points, or ambient closed-convex analytic structure.
\end{definition}

\begin{theorem}[Spectrahedron NameCert obligations]
\label{thm:spectrahedron-namecert-obligations}
For every accepted $\SpectrahedronUp$ carrier
$$
Q=(X,L,A,S,K,V,T,C,P,N),
$$
the local $\NameCert_{\SpectrahedronUp}$ surface consists exactly of carrier admission for the displayed parameter row $X$, linear-map row $L$, offset matrix row $A$, matrix-pencil row $S$, semidefinite-cone membership row $K$, convex-set provenance row $V$, componentwise $\hsame$ transport through $T$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:spectrahedron-carrier}. Its coordinates are the parameter, linear-map, offset, matrix-pencil, semidefinite-cone, convex-provenance, transport, replay, package, and local naming rows.

The affine-packet obligations are the rows $X,L,A,S$. They force every consumer to read the candidate point through a displayed $\VecSpaceUp$ parameter row, the $\LinearMapUp$ pencil direction, and the $\MatrixUp$ offset-and-sum surface.

The feasibility and convexity obligations are the rows $K$ and $V$. The semidefinite membership row is read through $\SemidefiniteConeUp$, while convex provenance is read through $\ConvexSetUp$ over the same parameter surface.

Finally $T,C,P,N$ transport, replay, source, and name the route. Since no other coordinate is present, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Spectrahedron semidefinite-cone handoff]
\label{thm:spectrahedron-semidefinite-cone-handoff}
Every feasibility-facing consumer of an accepted $\SpectrahedronUp$ carrier must factor through the displayed affine pencil route
$$
X,L,A \longmapsto S \longmapsto K \longmapsto V,T,C,P,N .
$$
Thus the consumer receives a parameter row, affine matrix-pencil row, semidefinite-cone membership row, convex-set provenance row, transport, replay, package provenance, and local NameCert rather than a host feasible set, spectral selector, determinant criterion, quotient matrix equality, selected feasible point, or ambient analytic closure theorem.
\end{theorem}
\begin{proof}
Begin with a feasibility-facing read of \autoref{def:spectrahedron-carrier}. The only route from a parameter row to matrix data is the displayed affine pencil formed by $L$ and $A$ and named by $S$.

Next read the cone-membership row $K$. Because $K$ is a $\SemidefiniteConeUp$ row over the displayed matrix pencil, the feasibility read cannot bypass the sibling semidefinite-cone carrier or replace it with a host positivity predicate.

The convex provenance row $V$ then records the accepted parameter surface as a $\ConvexSetUp$ consumer. The route remains tied to the same $\VecSpaceUp$, $\LinearMapUp$, $\MatrixUp$, and $\SemidefiniteConeUp$ rows.

Finally $T,C,P,N$ preserve and name the same finite route under transport and replay. No excluded analytic or host object is stored in the carrier, so every consumer factors through the displayed handoff.
\end{proof}

\closureat{SpectrahedronUp}{seedStr}

\begin{closurestatus}{\SpectrahedronUp}
  \constructivestory{A $\SpectrahedronUp$ packet is generated from an affine parameter row, LinearMap pencil row, Matrix offset row, matrix-pencil row, SemidefiniteCone membership row, ConvexSet provenance row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:spectrahedron-carrier}, \autoref{thm:spectrahedron-namecert-obligations}, and \autoref{thm:spectrahedron-semidefinite-cone-handoff} seed the affine semidefinite-feasibility route through parameter, pencil, cone, convex, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, spectral decomposition, determinant feasibility criteria, quotient equality of matrix pencils, selected feasible points, or ambient analytic closedness of semidefinite sections.}
  \upgradepath{Obligation closure requires checked carrier admission, affine-parameter visibility, linear-map pencil exactness, matrix offset and pencil replay, semidefinite-cone membership, convex-set provenance, transport stability, replay stability, and local naming for BEDC.Derived.SpectrahedronUp.}
\end{closurestatus}
