\begin{definition}[Banach complete-normed template obligations]
\label{def:banach-complete-normed-template-obligations}
The $\BanachUp$ complete-normed template is the following ten-field paper
target over the concrete carrier of
\autoref{def:banach-complete-normed-carrier}.
\begin{enumerate}
\item The traditional target is a complete normed vector space.
\item The BEDC source is $\NameCert_{\NormUp}$ together with
$\mathsf{CompleteMetricLimitWitness}$ for the norm-induced metric.
\item The carrier is the complete normed $\mathsf{BHist}$ predicate $C_V$.
\item The point classifier is the displayed Banach classifier $\sim_V$,
routed through $\hsame$ transport of representatives and ledgers.
\item The norm row is $\nu:C_V\to\RealUp$ with the RealUp classifier on norm
values.
\item The metric row is $d_\nu(x,y):=\nu(x-_V y)$, displayed as the
Banach metric witness consumed by $\CompleteMetricUp$.
\item Stability consists of norm transport, metric-distance transport, and
complete-metric limit transport across the classifier.
\item Exactness records zero norm-distance exactly on $\sim_V$-classified
endpoints and uniqueness of regular Cauchy limits up to $\sim_V$.
\item The ledger records the norm rows, stream observations, Cauchy moduli,
limit rows, metric-distance rows, and $\RatUp$ rational-comparison rows.
\item The status is a paper proof target for the $\BanachUp$ certificate
surface.
\end{enumerate}
\end{definition}

\begin{theorem}[Banach norm-completion source scope]
\label{thm:banach-norm-completion-source-scope}
For any $\BanachUp$ candidate of
\autoref{def:banach-complete-normed-carrier}, the complete normed carrier
supplies exactly the scoped $\BanachUp$ source obligations obtained from
$\NameCert_{\NormUp}$, $\StreamNameUp$, $\mathsf{MetricDistanceWitness}$,
$\mathsf{CompleteMetricLimitWitness}$, and $\hsame$. These obligations are
the carrier $C_V$, classifier $\sim_V$, norm $\nu$, norm-induced metric
$d_\nu$, regular Cauchy stream input, completion witness, transport rows, and
visible ledger fields named in
\autoref{def:banach-complete-normed-template-obligations}.
\end{theorem}
\begin{proof}
First read the metric row from the norm. Apply
\autoref{thm:banach-metric-induced-by-norm} to obtain the RealUp-valued
metric, zero exactness, symmetry, and triangle row for $d_\nu$.

Next read the stream and completion rows. Apply
\autoref{thm:banach-regular-cauchy-completion-obligation} to every regular
Cauchy $\StreamNameUp$ stream for $d_\nu$; the output is the carried limit,
the convergence modulus, and uniqueness up to $\sim_V$.

Transport is supplied by \autoref{thm:banach-hsame-transport}. It moves the
carried representatives, norm rows, metric rows, stream observations, modulus
histories, limit histories, and rational-comparison ledgers componentwise
across $\hsame$.

Finally apply \autoref{thm:banach-namecert-obligation-package}. Its fields
are exactly the carrier, classifier, norm-induced metric, regular Cauchy
input, complete-metric witness, transport, exactness, and ledger rows listed
above, so the source scope contains no additional Banach obligation.
\end{proof}

\begin{theorem}[Banach Hilbert downstream substrate]
\label{thm:banach-hilbert-downstream-substrate}
Let $H$ be a $\HilbertUp$ candidate whose inner-product norm induces the
displayed Banach norm $\nu$ on the carrier $C_V$. Then the Banach data
consumed by the Hilbert chapter are only the carrier $C_V$, the classifier
$\sim_V$, the norm-induced metric row $d_\nu$, and the
$\mathsf{CompleteMetricLimitWitness}$ family fixed by
\autoref{def:banach-complete-normed-template-obligations}. This substrate does
not assert Hilbert certificate closure or any operator theorem beyond those
rows.
\end{theorem}
\begin{proof}
Unpack the Hilbert input as an inner-product structure whose displayed norm
is the same $\nu$ used by the Banach candidate. The Banach carrier and
classifier are therefore copied directly as $C_V$ and $\sim_V$.

The metric field required downstream is the norm-induced row. By
\autoref{thm:banach-metric-induced-by-norm}, $d_\nu(x,y)=\nu(x-_V y)$ is the
metric row over the carried endpoints, and by
\autoref{thm:banach-classifier-transport-obligation} it respects the
classifier used by the Hilbert representative surface.

The completeness field is the same family consumed in
\autoref{thm:banach-regular-cauchy-completion-obligation}. Repack the carried
limit endpoint, convergence modulus, uniqueness row, and visible ledger as
the complete normed substrate named by the Hilbert chapter.

No inner-product law is inferred from these Banach rows. The Hilbert chapter
must still supply the inner-product carrier, sesquilinear rows, positivity,
and norm-induction proof at its own surface.
\end{proof}

\begin{theorem}[Banach bounded-operator source closure]
\label{thm:banach-bounded-operator-source-closure}
For $\BanachUp$ candidates $C,D$, the bounded-linear-operator carrier
$\mathsf{BanachBLOp}(C,D,T,K,\Lambda)$ of
\autoref{def:banach-bounded-linear-operator-carrier} is well-scoped over the
source and target Banach packages. Its endpoint action, bound row, Lipschitz
row, Cauchy-stream transport row, and ledger fields use only the carrier,
classifier, norm-induced metric, and completion data of $C$ and $D$.
\end{theorem}
\begin{proof}
Begin with the carrier of
\autoref{def:banach-bounded-linear-operator-carrier}. Its hypotheses already
name the source and target Banach carriers, their classifiers, their norms,
their induced distances, the endpoint map $T$, the RealUp bound $K$, and the
ledger $\Lambda$.

Apply \autoref{thm:banach-bounded-linear-operator-lipschitz}. The proof reads
both distances through \autoref{thm:banach-metric-induced-by-norm}, transports
the target difference across linearity of $T$, and uses the bound row in
$\Lambda$ to obtain the target distance estimate.

Apply \autoref{thm:banach-bounded-linear-operator-cauchy-transport} to a
regular Cauchy source stream. The transported observations are carried by
$D$, and the source modulus is converted into a target modulus using the
RealUp bound comparison for $K$.

Finally use \autoref{thm:banach-cauchy-stream-transport} for componentwise
$\hsame$ transport of stream observations, modulus histories, candidate
limits, distance rows, and rational-comparison ledgers. The resulting
operator package preserves the source closure data while landing in the
target Banach package, so the bounded-operator carrier is scoped over $C$ and
$D$ alone.
\end{proof}

\begin{closurestatus}{\BanachUp}
  \constructivestory{The concrete Banach surface begins with the singleton empty-history norm instance: the only vector endpoint is the empty history, every carried vector is classified with that endpoint, the norm value is the constant $\RealUp$ zero row, and the induced metric distance between any two carried endpoints is the same zero row. The classifier is the singleton vector classifier routed through $\hsame$ and the constant real classifier, so accepted presentations are the same exactly when their vector, norm, metric, stream, modulus, and limit ledgers transport through the displayed rows rather than through a host normed-space equality. The source specification is the consumed $\NormUp$ package together with $\StreamNameUp$ regular Cauchy inputs and $\mathsf{CompleteMetricLimitWitness}$ rows for the norm-induced metric, while the pattern specification records zero norm-distance exactness, Cauchy completeness with selected limit $\emp$, uniqueness of limits up to the singleton classifier, and bounded-operator limit transport over the same source and target Banach rows. The ledger policy keeps the singleton vector-space source, RatUp zero witness, constant-real seal, norm rows, metric-distance rows, Cauchy moduli, late-observation rows, selected limit, and bounded-operator transport evidence visible. The five name-certificate obligations are forced by the singleton: $\emp$ inhabits the carrier, reflexivity, symmetry, and transitivity come from $\hsame$ and the singleton classifier, and carrier closure is projection from any classified comparison because both endpoints already carry the same empty-history package. A history $h$ lies in the signature gap of a $\BanachUp$ token $p$ when the source-domain accepts it as this complete normed singleton package, the signature relation pairs it with an answer Banach row and evidence ledger, and the token-introduction relation names that answer as $p$; unfolded, $h$ carries the zero norm, zero metric, and constant-limit data encoded by $p$. The standard bridge maps the BEDC singleton Banach row to the one-point complete normed vector space and reads the unique standard point back as $\emp$, preserving soundness, completeness, and roundtrip classifier rows. The chapter registers this complete-normed singleton construction under the name $\BanachUp$; non-singleton Banach spaces, Hilbert closure, operator-algebra closure, and checked bridge data are not introduced.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature paper-side scope binds the singleton $\mathsf{SemanticNameCert}$ of \autoref{thm:banach-singleton-carrier-semantic-namecert}, the complete-normed source obligations of this section, the bounded-operator limit surface of \autoref{thm:banach-bounded-linear-operator-limit-namecert-surface}, and the singleton standard bridge soundness, completeness, and roundtrip rows of \autoref{thm:banach-singleton-standard-bridge-soundness}, \autoref{thm:banach-singleton-standard-bridge-completeness}, and \autoref{thm:banach-singleton-standard-bridge-roundtrip}.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.BanachUp.BanachSingleton\_standard\_bridge\_soundness}
  \bridgestatus{bridgeChecked}
  \notclaimed{This chapter does not claim bridgeChecked data, ordinary non-singleton Banach spaces, Hilbert closure, or operator-algebra closure.}
  \upgradepath{No further formal-axis work is recorded; the chapter is at the top formal status.}
\end{closurestatus}
