\section{Banach limit surface certificate}
\label{sec:banach-limit-surface-certificate}

\begin{definition}[Banach limit surface certificate]
\label{def:banach-limit-surface-certificate}
For a concrete Banach carrier $X$ of
\autoref{def:banach-concrete-carrier}, a regular $\StreamNameUp$ stream $s$,
a displayed modulus history $M$, a displayed limit history $\ell$, and a
late-distance ledger $\Lambda$, the Banach limit surface certificate is the
predicate
$$
\mathsf{BanachLimitSurface}_X(s,M,\ell,\Lambda).
$$
It consists of the carried $\mathsf{BHist}$ stream observations of $s$, the
componentwise $\hsame$ transport rows for the observations, the modulus
history $M$, and the limit history $\ell$, the displayed
$\mathsf{BanachMetricWitness}_X$ rows in $\Lambda$, and the
$\mathsf{CompleteMetricLimitWitness}(X,s,M,\ell,\Lambda)$ row that consumes
those distance rows.

The ten-field template is fixed as follows. The traditional target is the
Banach limit interface for regular Cauchy streams. The BEDC source is
$\NormUp$, $\StreamNameUp$, $\CompleteMetricUp$, and the $\RealUp$ comparison
rows used by the displayed norm distances. The carrier is the concrete Banach
carrier $X$. The classifier is $\hsame$ on carried representatives together
with the $\mathsf{RealClassifier}$ on norm distances. Stability is supplied by
\autoref{thm:banach-classifier-transport-obligation}. The ledger records the
stream observations, the modulus $M$, the endpoint $\ell$, the norm-distance
rows in $\Lambda$, and the $\RatUp$ comparison rows.

The core theorem list is
\autoref{thm:banach-limit-surface-endpoint-coverage},
\autoref{thm:banach-limit-surface-classifier-transport},
\autoref{thm:banach-limit-surface-uniqueness}, and
\autoref{thm:banach-limit-surface-namecert-obligations}. Exactness is the
equivalence between the displayed $\mathsf{BanachMetricWitness}_X$ rows and
the $\mathsf{CompleteMetricLimitWitness}$ rows they feed. The standard bridge
field is absent. The status is a paper proof target in
$\mathsf{BEDC.Derived.BanachUp}$.
\end{definition}

\begin{theorem}[Banach limit surface endpoint coverage]
\label{thm:banach-limit-surface-endpoint-coverage}
Any displayed row
$$
\mathsf{BanachLimitSurface}_X(s,M,\ell,\Lambda)
$$
exposes the carried Banach endpoint $X$, the carried $\StreamNameUp$
observations of $s$, the modulus history $M$, the carried limit history
$\ell$, every displayed $\mathsf{BanachMetricWitness}_X$ distance row in
$\Lambda$, and the corresponding
$\mathsf{CompleteMetricLimitWitness}(X,s,M,\ell,\Lambda)$ row.
\end{theorem}
\begin{proof}
Unfold \autoref{def:banach-limit-surface-certificate}. The first displayed
fields are exactly the carrier $X$, the stream observations of $s$, the
modulus history $M$, and the carried limit history $\ell$.

The next displayed fields are the ledger rows. Projecting them gives each
$\mathsf{BanachMetricWitness}_X$ distance row in $\Lambda$ together with the
$\RatUp$ comparison rows attached to the same late-observation entry.

The final displayed field is the consumed complete-metric row. Projecting it
gives $\mathsf{CompleteMetricLimitWitness}(X,s,M,\ell,\Lambda)$ with the same
carrier, stream, modulus, endpoint, and distance ledger.
\end{proof}

\begin{theorem}[Banach limit surface classifier transport]
\label{thm:banach-limit-surface-classifier-transport}
Let $\mathsf{BanachLimitSurface}_X(s,M,\ell,\Lambda)$ be displayed.
Componentwise $\hsame$ transport of the stream observations, modulus history,
limit endpoint, distance histories, and comparison ledgers preserves the
predicate $\mathsf{BanachLimitSurface}_X$ for the transported data.
\end{theorem}
\begin{proof}
Start with the stream and endpoint rows. Apply
\autoref{thm:banach-cauchy-stream-transport} to the transported observations,
modulus history, limit history, norm-distance rows, and $\RatUp$ comparison
rows. This keeps the regular Cauchy input and the convergence ledger in the
Banach complete-metric shape.

Next transport the norm and distance classifiers. For each carried endpoint
comparison in the stream and the candidate limit, use
\autoref{thm:banach-classifier-transport-obligation} to obtain the transported
$\mathsf{RealClassifier}$ rows for the corresponding norm values and induced
distances.

Finally repackage the transported complete-metric row. Apply
\autoref{thm:banach-complete-metric-namecert-coupling} to the transported
carrier rows, the transported $\mathsf{BanachMetricWitness}_X$ ledger, and the
transported $\mathsf{CompleteMetricLimitWitness}$ row. The resulting package
is precisely the transported $\mathsf{BanachLimitSurface}_X$ row.
\end{proof}

\begin{theorem}[Banach limit surface uniqueness]
\label{thm:banach-limit-surface-uniqueness}
Let $X$ be a concrete Banach carrier and let $s$ be a regular Cauchy
$\StreamNameUp$ stream over $X$. If
$$
\mathsf{BanachLimitSurface}_X(s,M_0,\ell_0,\Lambda_0)
$$
and
$$
\mathsf{BanachLimitSurface}_X(s,M_1,\ell_1,\Lambda_1)
$$
are displayed for the same stream, then the carried limit histories are
classified by $\hsame$. In the singleton empty-history carrier this
classification is the singleton classifier row
$\rho_{\emp}(\ell_0,\ell_1)$.
\end{theorem}
\begin{proof}
First project both surface rows through
\autoref{thm:banach-limit-surface-endpoint-coverage}. This exposes the two
complete-metric rows
$\mathsf{CompleteMetricLimitWitness}(X,s,M_0,\ell_0,\Lambda_0)$ and
$\mathsf{CompleteMetricLimitWitness}(X,s,M_1,\ell_1,\Lambda_1)$ for the same
regular Cauchy stream.

Apply \autoref{thm:banach-limit-uniqueness} to these two rows. Its conclusion
identifies the carried limit histories in the Banach point classifier, which
is the $\hsame$-classified representative relation fixed by
\autoref{def:banach-concrete-carrier}.

For the singleton carrier, read the same two projected rows through
\autoref{def:banach-complete-metric-namecert-interface}. Then apply
\autoref{thm:banach-singleton-limit-namecert-uniqueness}. It refines the
$\hsame$ classification of $\ell_0$ and $\ell_1$ to the displayed singleton
row $\rho_{\emp}(\ell_0,\ell_1)$.
\end{proof}

\begin{theorem}[Banach limit surface NameCert obligations]
\label{thm:banach-limit-surface-namecert-obligations}
The predicate $\mathsf{BanachLimitSurface}_X(s,M,\ell,\Lambda)$ together with
\autoref{thm:banach-limit-surface-endpoint-coverage},
\autoref{thm:banach-limit-surface-classifier-transport}, and
\autoref{thm:banach-limit-surface-uniqueness} assembles the paper-side
$\NameCert$ obligation package for Banach limit surfaces.
\end{theorem}
\begin{proof}
Endpoint coverage supplies the carrier, source, and ledger fields. By
\autoref{thm:banach-limit-surface-endpoint-coverage}, each certificate row
exposes the Banach carrier $X$, the $\StreamNameUp$ observations, the modulus
history, the carried endpoint, the Banach metric rows, the $\RatUp$ comparison
rows, and the complete-metric limit row.

Stability is supplied by classifier transport. Apply
\autoref{thm:banach-limit-surface-classifier-transport} to componentwise
$\hsame$ transport of the observations, modulus, endpoint, and ledger
histories; the theorem returns the transported Banach limit surface row with
the RealUp distance classifiers repacked.

Exactness is supplied by uniqueness and the displayed metric boundary. Apply
\autoref{thm:banach-limit-surface-uniqueness} for the limit endpoint
classifier, and read the metric rows through
\autoref{def:banach-limit-surface-certificate} to identify each
$\mathsf{BanachMetricWitness}_X$ row with the complete-metric row it feeds.

The CompleteMetricUp bridge is the interface of
\autoref{def:banach-complete-metric-namecert-interface}. It connects the
Banach norm-distance ledger to the consumed
$\mathsf{CompleteMetricLimitWitness}$ row, so the carrier, classifier,
stability, ledger, exactness, and bridge-facing fields of the Banach limit
surface $\NameCert$ package are all accounted for.
\end{proof}
