\begin{definition}[Banach root obligation source]
\label{def:banach-root-obligation-source}
The Banach root obligation source is the paper-side source tuple whose carrier
row is the concrete Banach carrier of \autoref{def:banach-concrete-carrier}.
Its distinguished concrete instance is the singleton carrier of
\autoref{def:banach-singleton-empty-history-instance}. Its metric row is the
norm-induced Banach metric witness of
\autoref{thm:banach-norm-induced-metric-compatibility}, and its completion row
is the complete-metric interface of
\autoref{def:banach-complete-metric-namecert-interface}.

Thus the root source names one surface object: a carried history predicate, the
$\hsame$ classifier on representatives, the norm-induced metric ledger, and
the regular Cauchy complete-metric witness family read at the Banach surface.
\end{definition}

\begin{theorem}[Banach root carrier-classifier obligation]
\label{thm:banach-root-carrier-classifier-obligation}
The Banach root obligation source of
\autoref{def:banach-root-obligation-source} supplies the carried history
predicate and the classifier transport field required by the
$\NameCert_{\BanachUp}$ surface. For the singleton root, the carried predicate
is the singleton empty-history carrier, and every accepted classifier
comparison transports the displayed carrier, vector, norm, and metric rows.
\end{theorem}
\begin{proof}
Start with the source tuple of
\autoref{def:banach-root-obligation-source}. Its carrier component is the
concrete Banach carrier of \autoref{def:banach-concrete-carrier}, so the
history predicate and the displayed norm rows are already part of the root
data.

For classifier transport, apply
\autoref{thm:banach-hsame-transport}. It moves carried representatives, norm
rows, induced metric rows, stream observations, modulus histories, limits, and
late-observation ledgers componentwise along $\hsame$.

In the singleton root, the carrier and classifier are fixed by
\autoref{def:banach-singleton-empty-history-instance} and
\autoref{thm:singleton-empty-history-norm-carrier-classifier}. Hence the
transport relation collapses to the singleton carrier comparison while still
preserving every displayed Banach row.
\end{proof}
\leanchecked{BEDC.Derived.BanachUp.BanachRoot\_carrier\_classifier\_obligation}

\begin{theorem}[Banach root norm-metric obligation]
\label{thm:banach-root-norm-metric-obligation}
The metric row carried by the Banach root obligation source is exactly the
norm-induced metric witness, and this row is stable under the Banach carrier
classifier. In the singleton root, the displayed distance between carried
histories $m,n:\mathsf{BHist}$ is the RealUp zero endpoint row precisely along
the singleton classifier comparison $\rho_{\emp}(m,n)$.
\end{theorem}
\begin{proof}
The metric component of the root source is defined to be the norm-induced
Banach metric row. Applying
\autoref{thm:banach-norm-induced-metric-compatibility} identifies the
singleton instance of this row with the constant RealUp zero endpoint exactly
on the singleton classifier comparison.

For a general Banach candidate, apply
\autoref{thm:banach-metric-induced-by-norm}. It reads the distance predicate
as the norm of a vector difference and supplies the metric laws demanded by the
complete-metric surface.

Stability under replacement of representatives is the content of
\autoref{thm:banach-classifier-transport-obligation}. The norm values and the
induced distances transport across the vector classifier, so the same metric
row remains valid after the carrier classifier is applied.
\end{proof}

\begin{theorem}[Banach root completion obligation]
\label{thm:banach-root-completion-obligation}
Every regular Cauchy $\StreamNameUp$ input accepted by the Banach root
obligation source has a carried Banach limit. Any two displayed limits for the
same accepted input are equal up to the Banach classifier, and in the singleton
root this classifier is the singleton empty-history classifier.
\end{theorem}
\begin{proof}
First read the accepted input through the complete-normed carrier surface.
\autoref{thm:banach-regular-cauchy-completion-obligation} supplies the
carried limit endpoint, convergence modulus, and uniqueness row for regular
Cauchy inputs over the induced metric.

Next place that displayed limit at the NameCert boundary. Apply
\autoref{thm:banach-complete-metric-namecert-coupling}; the complete-metric
row is accepted only through the Banach metric witness, so the produced package
does not leave the root surface.

For uniqueness in the concrete singleton root, apply
\autoref{thm:banach-singleton-limit-namecert-uniqueness}. It converts any two
Banach-surface complete-metric rows for the same stream into an $\hsame$
comparison of limits, and then into the singleton vector classifier
$\rho_{\emp}$.
\end{proof}

\begin{theorem}[Banach root NameCert surface]
\label{thm:banach-root-namecert-surface}
The Banach root obligation source assembles the paper-side
$\NameCert_{\BanachUp}$ surface. Its fields are the concrete carrier,
the $\hsame$ classifier on carried representatives, the norm-induced metric
row, the regular Cauchy completion row, the visible ledger for stream,
modulus, limit, norm, distance, and comparison histories, and an absent
standard-bridge slot. No ordinary Banach-space bridge is claimed by this root
surface.
\end{theorem}
\begin{proof}
The carrier and classifier fields are supplied by
\autoref{thm:banach-root-carrier-classifier-obligation}. They bind the root
surface to the carried history predicate and to componentwise $\hsame$
transport rather than to an external quotient.

The metric field is supplied by
\autoref{thm:banach-root-norm-metric-obligation}. It identifies the Banach
distance slot with the norm-induced metric witness and records that this row
is stable under classifier transport.

The completion field is supplied by
\autoref{thm:banach-root-completion-obligation}. It turns every accepted
regular Cauchy stream into a carried limit and records uniqueness up to the
Banach classifier.

The ledger fields are exactly the rows named in
\autoref{def:banach-root-obligation-source}: carrier histories, stream
observations, modulus histories, limit histories, norm rows, distance rows,
and rational comparison rows. Since the source names no ordinary
Banach-space bridge, the standard-bridge row is absent and the root surface is
the concrete BEDC obligation package used by downstream Hilbert, topology, and
bounded-operator consumers.
\end{proof}
