\begin{definition}[Singleton Banach standard bridge surface]
\label{def:banach-singleton-standard-bridge-surface}
The standard comparison object for the singleton Banach certificate is the
one-point complete normed vector space $B_{\star}=\{\star\}$ over the one-point
scalar action, with zero vector $\star$, zero norm
$\lVert\star\rVert=0_{\mathsf{Real}}^{c}$, zero metric
$d_{\star}(\star,\star)=0_{\mathsf{Real}}^{c}$, and the unique complete-metric
limit operation sending every regular Cauchy stream to $\star$.

The BEDC side is the singleton empty-history carrier of
\autoref{def:banach-singleton-empty-history-instance}. Its carrier is
$A_{\emp}$, its classifier is $\rho_{\emp}$, its norm and metric endpoints are
the constant RealUp zero endpoint, and its convergence rows are the displayed
$\mathsf{CompleteMetricLimitWitness}$ rows supplied by
\autoref{thm:banach-regular-cauchy-limit-witness}. The bridge maps every
carried BEDC vector history to $\star$, and maps $\star$ back to $\emp$ with
the carrier, norm, metric, and limit ledgers read through the singleton
classifier.
\end{definition}

\begin{theorem}[Singleton Banach bridge soundness]
\label{thm:banach-singleton-standard-bridge-soundness}
Every carried BEDC singleton Banach row of
\autoref{def:banach-singleton-empty-history-instance} maps to the unique point
$\star$ of $B_{\star}$. Under this map, the displayed vector is classified by
$\rho_{\emp}$, its norm and induced metric distance are the constant RealUp
zero endpoint, and every regular Cauchy stream carries complete-metric
convergence data to the constant standard limit $\star$.
\end{theorem}
\begin{proof}
First collapse the carried vector row. By
\autoref{thm:banach-singleton-empty-history-carrier-classifier}, every carried
Banach vector lies in $A_{\emp}$ and every pair of carried singleton vectors is
$\rho_{\emp}$-classified. The bridge therefore has only one possible standard
image, namely $\star$.

Next read the metric data. The norm-induced compatibility theorem
\autoref{thm:banach-norm-induced-metric-compatibility} identifies the
singleton Banach metric row with the constant RealUp zero endpoint exactly on
the same classifier row. Thus the standard norm and standard distance both
receive the zero value required by $B_{\star}$.

Finally transport the convergence ledger. For a regular Cauchy stream,
\autoref{thm:banach-regular-cauchy-limit-witness} supplies a displayed
$\mathsf{CompleteMetricLimitWitness}$ row whose selected limit, modulus
history, and late-distance rows are all singleton rows. Applying the bridge to
each component sends that row to the unique complete-metric limit datum of the
one-point standard object.
\end{proof}
\leanchecked{BEDC.Derived.BanachUp.BanachSingleton\_standard\_bridge\_soundness}

\begin{theorem}[Singleton Banach bridge completeness]
\label{thm:banach-singleton-standard-bridge-completeness}
The unique standard point $\star$ maps back to $\emp$ and reconstructs the
singleton BEDC Banach surface: carrier $A_{\emp}$, classifier $\rho_{\emp}$,
constant zero norm, constant zero metric, and the singleton
$\mathsf{CompleteMetricLimitWitness}$ family.
\end{theorem}
\begin{proof}
Unpack the bridge surface of
\autoref{def:banach-singleton-standard-bridge-surface}. Its reverse map sends
the only standard point to $\emp$, and the BEDC carrier row is precisely the
singleton empty-history carrier of
\autoref{def:banach-singleton-empty-history-instance}.

The reconstructed completeness data are the singleton data. Apply
\autoref{thm:banach-singleton-empty-history-cauchy-completeness}: every
regular Cauchy stream in the singleton Banach metric has selected limit
$\emp$, and every distance to that limit is classified by the constant RealUp
zero endpoint.

It remains to identify the displayed limit row chosen by the bridge with any
other singleton limit presentation. Use
\autoref{thm:banach-singleton-limit-namecert-uniqueness}; it gives
$\hsame$-equality of singleton Banach limits, and the singleton classifier
repackages that equality as $\rho_{\emp}$. Hence the reverse image reconstructs
the same carrier, norm, metric, and limit witness surface.
\end{proof}
\leanchecked{BEDC.Derived.BanachUp.BanachUp\_StdBridge}

\begin{theorem}[Singleton Banach bridge roundtrip]
\label{thm:banach-singleton-standard-bridge-roundtrip}
For the bridge of
\autoref{def:banach-singleton-standard-bridge-surface}, the composite
BEDC-to-standard-to-BEDC is $\rho_{\emp}$ on carried singleton histories, and
the composite standard-to-BEDC-to-standard is the identity on the one-point
complete normed vector space $B_{\star}$.
\end{theorem}
\begin{proof}
For the BEDC composite, start with a carried singleton Banach history. The
soundness theorem
\autoref{thm:banach-singleton-standard-bridge-soundness} sends it to the
unique standard point $\star$, and the completeness theorem
\autoref{thm:banach-singleton-standard-bridge-completeness} sends $\star$ back
to $\emp$ with the singleton carrier and zero ledgers.

The classifier comparison is exactly the singleton collapse. By
\autoref{thm:banach-singleton-empty-history-carrier-classifier}, every carried
source history is $\rho_{\emp}$-classified with $\emp$, so the BEDC composite
acts as $\rho_{\emp}$ on carried histories.

For the standard composite, there is only one point of $B_{\star}$. The reverse
map selects $\emp$, and soundness maps that BEDC point back to $\star$. Since
$\star$ is the unique standard point, the composite is the identity on the
one-point complete normed vector space.
\end{proof}
\leanchecked{BEDC.Derived.BanachUp.BanachSingleton\_standard\_bridge\_roundtrip}

\begin{lemma}[Singleton Banach standard bridge determinacy]
\label{lem:banach-singleton-standard-bridge-determinacy}
For the bridge surface of
\autoref{def:banach-singleton-standard-bridge-surface}, every consumer-facing
route, transport, readback, or limit handoff is determined by the displayed
singleton rows. The BEDC-to-standard route factors through the singleton carrier
$A_{\emp}$ and classifier $\rho_{\emp}$, the standard-to-BEDC readback factors
through the selected endpoint $\emp$, the norm and metric transports factor
through the constant RealUp zero endpoint, and every complete-metric handoff
factors through the displayed
$\mathsf{CompleteMetricLimitWitness}$ rows of
\autoref{thm:banach-regular-cauchy-limit-witness}. No unlisted bridge
coordinate supplies an additional carrier point, distance value, classifier, or
limit datum.
\end{lemma}
\begin{proof}
Unpack the bridge surface of
\autoref{def:banach-singleton-standard-bridge-surface}. Its standard object is
the one-point complete normed vector space $B_{\star}=\{\star\}$, and its BEDC
object is the singleton empty-history carrier of
\autoref{def:banach-singleton-empty-history-instance}. Hence a forward route
has only one standard codomain point available. By
\autoref{thm:banach-singleton-standard-bridge-soundness}, every carried BEDC
singleton Banach row maps to that point $\star$, and the displayed source row is
read through $A_{\emp}$ and $\rho_{\emp}$. Thus any accepted forward use factors
through the same singleton carrier and classifier rows; there is no second
standard endpoint through which it could factor.

The readback side is equally fixed by the displayed bridge surface. The only
standard point $\star$ is sent back to $\emp$, and the reverse ledger is stated
there with the carrier, norm, metric, and limit data read through the singleton
classifier. Since the reverse map has no other standard input and names no
other BEDC endpoint, any consumer readback is the selected row $\emp$ together
with its $\rho_{\emp}$ carrier comparison.

For norm and metric transport, soundness identifies the norm of the displayed
vector and every induced metric distance with the constant RealUp zero endpoint.
This is precisely the local norm-induced metric route supplied by
\autoref{thm:banach-norm-induced-metric-compatibility}: the singleton metric row
is accepted on the same $\rho_{\emp}$ classifier row and is classified by the
constant RealUp zero endpoint. Therefore a consumer cannot choose an anonymous
distance coordinate or a second metric classifier; every distance read is the
same zero row already present in the singleton Banach surface.

It remains to check complete-metric handoff. Soundness sends every regular
Cauchy stream to the constant standard limit $\star$, while
\autoref{thm:banach-regular-cauchy-limit-witness} supplies the displayed
$\mathsf{CompleteMetricLimitWitness}$ row whose selected limit, modulus history,
and late-distance ledgers are singleton rows. Applying the bridge componentwise
therefore leaves only that listed limit package: selected limit $\emp$ on the
BEDC side, selected limit $\star$ on the standard side, empty singleton modulus,
and late-distance rows classified by the constant RealUp zero endpoint. These
are exactly the rows exposed in
\autoref{def:banach-singleton-standard-bridge-surface} and used by
\autoref{thm:banach-singleton-standard-bridge-soundness}. Since the surface
lists no further carrier, transport, metric, or limit coordinate, any alleged
unlisted bridge coordinate has no displayed row from which a consumer-facing use
could be read.
\end{proof}

\begin{corollary}[Singleton Banach standard bridge consumer determinacy]
\label{cor:banach-singleton-standard-bridge-consumer-determinacy}
Fix the bridge surface of
\autoref{def:banach-singleton-standard-bridge-surface}. Any accepted
consumer use of the singleton Banach standard bridge has the same exposed
finite decision as the chapter rows: a forward use chooses the singleton
standard route, a readback use chooses the singleton BEDC endpoint route, a
norm or metric use chooses the constant $\RealUp$ zero exactness row, and a
complete-metric use chooses the displayed singleton limit-witness package. In
particular, the bridge exports no hidden coordinate, no alternate normal form,
and no duplicate classifier source for the singleton Banach object.
\end{corollary}
\begin{proof}
The bridge surface in
\autoref{def:banach-singleton-standard-bridge-surface} names all rows available
to a consumer: the one-point standard comparison object, the singleton BEDC
carrier and classifier, the constant $\RealUp$ zero norm and metric endpoints,
and the displayed complete-metric limit-witness rows. Apply
\autoref{lem:banach-singleton-standard-bridge-determinacy} to this fixed
surface. It states that every consumer-facing route, transport, readback, or
limit handoff factors through exactly those displayed singleton rows and that
no unlisted bridge coordinate supplies an additional carrier point, distance
value, classifier, or limit datum.

Thus the forward route cannot select anything other than the singleton
standard point named by the surface, and the readback route cannot select
anything other than the singleton BEDC endpoint named by the surface. The norm
and metric transports cannot introduce a second exactness decision, because
the determinacy lemma forces them through the same constant $\RealUp$ zero row
already exposed by the bridge definition. Likewise a complete-metric handoff
cannot select a detached modulus, tail, late-distance, or limit coordinate:
the only accepted package is the displayed singleton limit-witness package
cited by the surface and by the determinacy lemma.

These four cases exhaust the consumer-facing uses listed in the determinacy
lemma. Therefore, once the bridge surface rows are fixed, every accepted
consumer use picks the same finite route, readback normal form, or exactness
decision named by the singleton Banach chapter, and there is no further hidden
coordinate or duplicate classifier source.
\end{proof}
