\begin{theorem}[Helly finite-subfamily ledger route]
\label{thm:helly-theorem-finite-subfamily-ledger-route}
Every $\HellyTheoremUp$ finite-subfamily ledger consumed by $\CaratheodoryConvexHullUp$ must read $\ConvexSetUp$ membership rows, $\PolytopeUp$ finite witness rows, $\AffineSpaceUp$ and $\VecSpaceUp$ ambient rows, and $\CompactMetricUp$ finite-read boundaries before exporting the bounded support surface. The ledger route is therefore
$$
\AffineSpaceUp,\VecSpaceUp \longmapsto \ConvexSetUp \longmapsto \PolytopeUp,\CompactMetricUp \longmapsto \CaratheodoryConvexHullUp .
$$
It exposes only the named finite subfamily data and does not introduce a host separation theorem, a selected intersection point, quotient convex-set equality, or ambient standard-model convexity.
\end{theorem}
\begin{proof}
Project the existing $\HellyTheoremUp$ carrier of \autoref{def:helly-theorem-carrier}. Its ambient rows are $A,V$, its convex-family row is $F$, and its finite witness and subfamily rows are $W,S,I$.

Follow the sibling route already displayed by the chapter: $\ConvexSetUp$ supplies membership rows, $\PolytopeUp$ supplies finite witnesses, $\AffineSpaceUp$ and $\VecSpaceUp$ supply the ambient affine and displacement rows, and $\CompactMetricUp$ supplies the finite-read boundary. The $\CaratheodoryConvexHullUp$ consumer can read a bounded support surface only after those rows have been displayed.

No carrier coordinate stores host separation, a selected intersection point, quotient convex-set equality, or ambient standard-model convexity. The exported ledger is therefore exactly the finite sibling route stated above.
\end{proof}

\begin{proposition}[Helly convex-hull sibling dependency]
\label{prop:helly-theorem-convex-hull-sibling-dependency}
The $\HellyTheoremUp$ finite-intersection certificate supplies its convex-hull dependency only through the finite subfamily ledger consumed by \autoref{ch:concrete-instances-caratheodory-convex-hull-namecert}. Thus any Caratheodory convex-hull readback using $\HellyTheoremUp$ must display the convex-family classifier, finite witness ledger, full-family intersection row, and local NameCert provenance before the Caratheodory finite-generation route may expose bounded support data.
\end{proposition}
\begin{proof}
Use \autoref{thm:helly-theorem-finite-subfamily-ledger-route}. It already forces the Helly ledger through the convex-family, polytope, affine, vector, and compact finite-read rows before the Caratheodory convex-hull surface is available.

The sibling chapter \autoref{ch:concrete-instances-caratheodory-convex-hull-namecert} then consumes that ledger as its Helly handoff row. Since neither the Helly carrier nor the Caratheodory convex-hull carrier stores a host separation theorem, selected intersection point, or quotient convex-hull equality, the dependency remains the displayed finite-generation route and nothing larger.
\end{proof}
