\chapter{Finite Cauchy Diagonal NameCert Construction}
\label{ch:concrete-instances-finite-cauchy-diagonal-namecert}
\origin{human}

Following Bishop and Bridges, the $\FiniteCauchyDiagonalUp$ packet records the finite diagonal selector needed when a displayed Cauchy family is read through regular rational windows and then sealed as a real name. It sits between the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet supplies only a finite selector surface for completion and Real consumers; it does not choose an infinite subsequence, a quotient representative, or a host limit.

\begin{definition}[Finite Cauchy diagonal carrier]
\label{def:finite-cauchy-diagonal-carrier}
A $\FiniteCauchyDiagonalUp$ carrier is a finite $\BHist$ packet
$$
D=(F,W,K,S,R,Y,E,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $F$ is the finite family row, naming the displayed Cauchy sources whose diagonal window is requested.
\item $W$ is the selected-window classifier row, recording the finite window chosen for each displayed precision request and each displayed source row.
\item $K$ is the classifier-stability row, comparing selected windows only by the same $\hsame$ and $\Cont$ routes used by the source family.
\item $S$ is the $\StreamNameUp$ observation schedule exposed by the selected windows.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from $S$.
\item $Y$ is the $\DyadicRatCoreUp$ tolerance ledger that bounds the diagonal comparisons.
\item $E$ is the terminal $\RealUp$ seal handoff, available only after $F,W,K,S,R,Y$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the family, window, stability, stream, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for diagonal-selection requests through $F,W,K,S,R,Y,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteCauchyDiagonalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteCauchyDiagonalUp}$ row.
\end{enumerate}
The classifier reads only $F,W,K,S,R,Y,E,H,C,P,N$. There is no coordinate for countable choice, a selected infinite diagonal sequence, quotient stream equality, host sequence equality, selected limits, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Finite Cauchy diagonal NameCert obligations]
\label{thm:finite-cauchy-diagonal-namecert-obligations}
For every accepted $\FiniteCauchyDiagonalUp$ carrier $D=(F,W,K,S,R,Y,E,H,C,P,N)$, the local $\NameCert_{\FiniteCauchyDiagonalUp}$ surface consists exactly of five obligation rows:
\begin{enumerate}
\item finite diagonal carrier admission through the displayed family row $F$;
\item selected-window classifier admission through $W$, with one displayed finite window for each displayed precision request and source row;
\item classifier stability through $K,H,C$, preserving the selected windows under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item diagonal extraction ledger admission through $S,R,Y$, requiring every extracted read to pass through the same $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ rows;
\item $\RealUp$ seal handoff through $E$, requiring the finite family, selected-window classifier, stability row, stream schedule, readback row, dyadic ledger, transport, replay, provenance, and local naming to remain visible to the terminal real-name consumer.
\end{enumerate}
No obligation row certifies countable choice, a selected infinite diagonal sequence, quotient stream equality, host sequence equality, selected limits, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-cauchy-diagonal-carrier}. The visible rows are exactly $F,W,K,S,R,Y,E,H,C,P,N$, so the finite family and selected-window classifier are the only routes by which a diagonal request enters the packet.

The stability row is read before any terminal seal. Transport by $H$ and replay by $C$ preserve the same family row, selected-window row, and classifier-stability row, so a replayed request cannot replace the finite selector by an infinite choice schedule or by host sequence equality.

The extraction ledger is then read through $S,R,Y$. The stream schedule supplies finite observations, the regular rational row repacks those observations, and the dyadic row records the tolerance budget for the same displayed windows.

Finally the Real handoff is downstream from the ledger. Since $E$ is available only after $F,W,K,S,R,Y,H,C,P,N$ have been displayed, every $\RealUp$ or completion-facing consumer receives a finite diagonal selector surface rather than a hidden limit or quotient representative.
\end{proof}

\falsifiablePrediction{An accepted $\FiniteCauchyDiagonalUp$ read is refuted if the Real-facing diagonal handoff reaches $\RealUp$ without displaying the finite family row, selected-window classifier, classifier-stability row, StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, transport, replay, provenance, and local naming rows.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real: $\FiniteCauchyDiagonalUp$ is not bijective to any listed sibling because it jointly carries finite family admission, selected-window classification, classifier stability, diagonal extraction, Real seal handoff, transport, replay, provenance, and local naming as one packet.}

\closureat{FiniteCauchyDiagonalUp}{seedStr}

\begin{closurestatus}{\FiniteCauchyDiagonalUp}
  \constructivestory{A $\FiniteCauchyDiagonalUp$ packet is generated from a displayed finite Cauchy family, selected finite windows, classifier-stability rows, StreamName observations, RegSeqRat readback, a DyadicRatCore tolerance ledger, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-cauchy-diagonal-carrier} and \autoref{thm:finite-cauchy-diagonal-namecert-obligations} seed the finite diagonal selector route over family, selected-window, stability, StreamName, RegSeqRat, DyadicRatCore, RealUp seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim countable choice, a selected infinite diagonal sequence, quotient stream equality, host sequence equality, selected limits, Lean verification, bridge checking, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, selected-window classifier admission, classifier stability, diagonal extraction, RealUp seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.FiniteCauchyDiagonalUp.}
\end{closurestatus}
