\chapter{A Concrete Naming Certificate for $\BioRealityQSixLeaveOneCodonBoundaryUp$}
\label{ch:concrete-instances-bioreality-q-six-leave-one-codon-boundary-namecert}
\origin{ai}

The $\BioRealityQSixLeaveOneCodonBoundaryUp$ packet names the finite boundary surface for the $h1$ leave-one-codon query-six evaluation. The displayed empirical surface has no anchor rows, exactly $5$ boundary rows, $8$ high-coverage rows, $8$ predictable rows, recovery rate $1.0$, and recovery rate above threshold $1.0$. The chapter therefore records a boundary condition for a finite table evaluation: the carrier says that all predictable rows are recovered at the displayed threshold while the anchor side is empty and the boundary side contains five rows. It does not infer a codon-level mechanism, biological causation, a p-value, or an unlisted codon table.

\begin{definition}[BioRealityQSixLeaveOneCodonBoundary carrier]
\label{def:bioreality-q-six-leave-one-codon-boundary-carrier}
A $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier is a finite $\BHist$ packet
$$
\begin{gathered}
L=(A,B,H,Q,R,S,T,C,P,N)
\end{gathered}
$$
with the following displayed rows:
\begin{itemize}
\item $A$ is the anchor-count row asserting exactly $0$ anchors;
\item $B$ is the boundary-count row asserting exactly $5$ boundary rows;
\item $H$ is the high-coverage row asserting exactly $8$ rows at the high-coverage boundary surface;
\item $Q$ is the predictable-count row asserting exactly $8$ predictable rows;
\item $R$ is the recovery-rate row with value $1.0$;
\item $S$ is the above-threshold recovery-rate row with value $1.0$;
\item $T$ is the verification-time row recording that these displayed rows were verified at $2026$-$05$-$26\,16\!:22\!:47+00\!:00$;
\item $C$ is the componentwise $\hsame$ transport and displayed $\Cont$ replay row for $A,B,H,Q,R,S,T$;
\item $P$ is the $\Pkg$ provenance row for this finite BioReality leave-one-codon boundary evaluation;
\item $N$ is the local $\NameCert_{\BioRealityQSixLeaveOneCodonBoundaryUp}$ row naming exactly this packet.
\end{itemize}
The carrier has no slot for a codon list, witness label, p-value, causal model, hidden anchor, additional boundary row, or recovery statistic beyond the displayed values $0$, $5$, $8$, $8$, $1.0$, and $1.0$.
\end{definition}

\begin{theorem}[Leave-one-codon boundary NameCert obligations]
\label{thm:bioreality-q-six-leave-one-codon-boundary-namecert-obligations}
For every accepted $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier $L=(A,B,H,Q,R,S,T,C,P,N)$, the local $\NameCert_{\BioRealityQSixLeaveOneCodonBoundaryUp}$ surface consists exactly of anchor-count exposure through $A$, boundary-count exposure through $B$, high-coverage exposure through $H$, predictable-count exposure through $Q$, recovery-rate exposure through $R$, above-threshold recovery exposure through $S$, verification-time exposure through $T$, transport and replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}

\begin{proof}
Inspect an accepted carrier $L$. The first two rows fix the boundary shape: $A$ exposes $0$ anchors and $B$ exposes $5$ boundary rows. The next two rows fix the row counts available to the recovery reading: $H$ exposes $8$ high-coverage rows and $Q$ exposes $8$ predictable rows. The rate rows expose the only two recovery values carried by the packet, namely $R=1.0$ and $S=1.0$. The timestamp row $T$ fixes when those displayed values were verified, while $C,P,N$ only transport, replay, source, and name the same finite packet. Since the carrier contains no additional codon table, p-value, hidden witness, causal model, or extra row count, no further NameCert obligation can be read from it.
\end{proof}

\begin{theorem}[Zero-anchor five-boundary reading]
\label{thm:bioreality-q-six-leave-one-codon-boundary-zero-anchor-five-boundary}
Inside an accepted $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier, the named boundary surface has empty anchor side and five displayed boundary rows:
$$
\begin{aligned}
A&=0,\\
B&=5.
\end{aligned}
$$
Consequently the packet names a boundary-only obstruction surface for this finite evaluation, not a paired anchor-boundary ledger.
\end{theorem}

\begin{proof}
The values $A=0$ and $B=5$ are displayed carrier rows. A carrier row with zero anchors supplies no anchor-side witness for the local NameCert surface. The boundary-count row supplies exactly five boundary entries. Therefore the only licensed reading is a five-row boundary surface with no anchor rows in this packet.
\end{proof}

\begin{theorem}[Complete recovery reading]
\label{thm:bioreality-q-six-leave-one-codon-boundary-complete-recovery}
Inside an accepted $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier, the high-coverage row count and predictable row count agree, and both recovery rates are exactly $1.0$:
$$
\begin{aligned}
H&=8,\\
Q&=8,\\
R&=1.0,\\
S&=1.0.
\end{aligned}
$$
Thus the named packet records complete recovery for the displayed $8$ predictable rows at the displayed threshold.
\end{theorem}

\begin{proof}
The rows $H$ and $Q$ both display the count $8$. The rows $R$ and $S$ both display the value $1.0$. Since these are carrier coordinates, componentwise NameCert preservation keeps the high-coverage count, predictable count, raw recovery rate, and above-threshold recovery rate together. No stronger numerical claim is introduced; the theorem only reads the displayed equality of the finite counts and the two displayed recovery values.
\end{proof}

\begin{theorem}[No codon mechanism escape]
\label{thm:bioreality-q-six-leave-one-codon-boundary-nonescape}
An accepted $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier does not certify a codon-level mechanism, codon list, p-value, hidden witness, biological causation claim, additional anchor, additional boundary row, or recovery rate outside the displayed rows $A,B,H,Q,R,S,T,C,P,N$.
\end{theorem}

\begin{proof}
Every exported datum of the carrier appears in one of the listed rows. The rows list the anchor count, boundary count, high-coverage count, predictable count, two recovery rates, verification time, transport and replay, provenance, and local naming. None of those rows contains a codon list, p-value, mechanism field, hidden witness field, or further empirical table. Such data therefore cannot be exported by the local NameCert surface.
\end{proof}

\falsifiablePrediction{If a later replay keeps the same $\BioRealityQSixLeaveOneCodonBoundaryUp$ carrier name but changes the anchor count from $0$, the boundary count from $5$, either displayed count $8$, or either recovery value $1.0$, then it is not the same finite packet under componentwise NameCert preservation.}

\independenceWitness{q-six-leave-one-codon-boundary: the carrier is separated by the simultaneous presence of anchor count $0$, boundary count $5$, high-coverage count $8$, predictable count $8$, recovery rate $1.0$, above-threshold recovery rate $1.0$, and the verification-time row. Removing any one of these rows yields a different empirical boundary packet rather than a bijective copy of this certificate.}

\closureat{BioRealityQSixLeaveOneCodonBoundaryUp}{seedStr}

\begin{closurestatus}{\BioRealityQSixLeaveOneCodonBoundaryUp}
  \constructivestory{A $\BioRealityQSixLeaveOneCodonBoundaryUp$ packet is generated from a zero-anchor count row, a five-boundary count row, two displayed count rows with value $8$, two displayed recovery-rate rows with value $1.0$, a verification-time row, componentwise $\hsame$ transport with displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the carrier, NameCert obligation surface, zero-anchor five-boundary reading, complete-recovery reading, non-escape theorem, falsifiable prediction, and independence witness for the finite BioReality query-six leave-one-codon boundary packet.}
  \formalstatus{\unformalized}
  \bridgestatus{none}
  \notclaimed{The chapter does not claim codon-level mechanism, p-value significance, a codon list, a hidden witness name, additional anchors, additional boundary rows, additional predictable rows, or biological causation beyond the displayed empirical ledger.}
  \upgradepath{A stronger status requires a checked bridge that imports the anchor-count row, boundary-count row, high-coverage count, predictable count, recovery-rate rows, and verification-time row into a formal carrier without adding data outside the displayed packet.}
\end{closurestatus}