\begin{theorem}[Tagged option source weakening]
\label{thm:tagged-option-source-weakening}
This theorem fits the per-object template as follows: the traditional target is
tagged option source weakening; the BEDC source is $\mathsf{BHist}$ with
$\hsame$; the carrier is $\mathsf{TaggedOptionHistoryCarrier}$; the classifier
is $\mathsf{TaggedOptionHistoryClassifier}$; the stability field is source
monotonicity for tagged endpoints; the ledger is the visible absent/present tag
with present payload evidence; the core theorem is tagged source weakening;
exactness is endpoint witness preservation; the standard bridge is constructor
tagged option syntax; and the status is $\mathsf{ProofTarget}$. Let
$S,T:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC history source carriers, and let
$\sim_S$ and $\sim_T$ be source classifiers. Assume
$$
\forall h.\; S(h)\to T(h)
$$
and
$$
\forall a\,b.\; S(a)\to S(b)\to a\sim_S b\to a\sim_T b.
$$
Then for every history $h$,
$$
\mathsf{TaggedOptionHistoryCarrier}_S(h)\to
\mathsf{TaggedOptionHistoryCarrier}_T(h),
$$
and for every pair of histories $h,k$,
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)\to
\mathsf{TaggedOptionHistoryClassifier}_{T,\sim_T}(h,k).
$$
\end{theorem}
\begin{proof}
For the carrier implication, split the tagged carrier witness. The absent case
has no source payload and is reused unchanged. The present case exposes a
payload history $a$, a source witness $S(a)$, and the endpoint witness
$\hsame(h,\Eone(a))$; apply the source-carrier implication to obtain $T(a)$ and
reuse the same endpoint witness.

For the classifier implication, split the tagged classifier witness. The
absent-absent case is reused unchanged. In the present-present case, keep the
payload histories $a,b$ and both endpoint witnesses. Apply the source-carrier
implication to the two source witnesses to obtain $T(a)$ and $T(b)$, and apply
the source-classifier implication to the same two source witnesses and the
given $a\sim_S b$ witness to obtain $a\sim_T b$. These fields rebuild the
tagged classifier witness for $T$ and $\sim_T$.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.TaggedOptionHistorySource\_weakening}

\begin{theorem}[Tagged option semantic fields source weakening]
\label{thm:tagged-option-semantic-fields-source-weakening}
Let $S,T:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC history source carriers, and
let $\sim_S$ and $\sim_T$ be source classifiers. Assume
$$
\forall h.\; S(h)\to T(h)
$$
and
$$
\forall a\,b.\; S(a)\to S(b)\to a\sim_S b\to a\sim_T b.
$$
Then for every history $h$, the three unary tagged option semantic fields
transport from $S$ to $T$:
$$
\mathsf{TaggedOptionHistoryCarrier}_S(h)\to
\mathsf{TaggedOptionHistoryCarrier}_T(h),
$$
$$
\mathsf{TaggedOptionHistoryPattern}_S(h)\to
\mathsf{TaggedOptionHistoryPattern}_T(h),
$$
and
$$
\mathsf{TaggedOptionHistoryLedger}_S(h)\to
\mathsf{TaggedOptionHistoryLedger}_T(h).
$$
The binary classifier field transports separately:
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)\to
\mathsf{TaggedOptionHistoryClassifier}_{T,\sim_T}(h,k).
$$
\end{theorem}
\begin{proof}
Apply Theorem~\ref{thm:tagged-option-source-weakening} to the displayed
source-carrier and source-classifier implications. This gives the carrier
transport and classifier transport directly. For the pattern field, use
Theorem~\ref{thm:tagged-option-history-carrier-pattern-ledger-equivalence} to
convert a $\mathsf{TaggedOptionHistoryPattern}_S(h)$ witness into the
$S$-carrier witness, transport that carrier witness from $S$ to $T$, and convert
the resulting $T$-carrier witness back to
$\mathsf{TaggedOptionHistoryPattern}_T(h)$. The ledger field is identical, using
the ledger half of the same carrier-pattern-ledger equivalence.
\end{proof}

\begin{definition}[Tagged option payload descent relation]
\label{def:tagged-option-payload-descent-relation}
Let $S,T:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC history source carriers, let
$\sim_S$ and $\sim_T$ be source classifiers, let
$\delta:\mathsf{DescentCertificate}(\mathsf{BHist},\mathsf{BHist},\sim_S,\sim_T)$,
and assume payload-carrier preservation
$$
\rho_{\delta}:\forall a.\;S(a)\to T(\delta.\mathsf{map}(a)).
$$
The relation $\mathsf{TaggedOptionMapRel}_{\delta}(S,T,\rho_{\delta};h,k)$
means that the tagged endpoint $h$ over $S$ is carried to the tagged endpoint
$k$ over $T$ by preserving the visible option tag:
$$
\mathsf{TaggedOptionMapRel}_{\delta}(S,T,\rho_{\delta};h,k)
\Longleftrightarrow
\bigl(\hsame(h,\emp)\land\hsame(k,\emp)\bigr)
\lor
\bigl(\exists a:\mathsf{BHist}.\;
S(a)\land T(\delta.\mathsf{map}(a))\land
\hsame(h,\Eone(a))\land
\hsame(k,\Eone(\delta.\mathsf{map}(a)))\bigr).
$$
The displayed $T(\delta.\mathsf{map}(a))$ witness is the carrier preservation
field $\rho_{\delta}$ applied to the exposed source payload.
\end{definition}
\leandef{BEDC.Derived.OptionUp.TaggedOptionMapRel}

\begin{theorem}[Tagged option map relation visible branch equivalence]
\label{thm:tagged-option-maprel-visible-branch-equivalence}
This theorem fits the per-object template as follows: the traditional target is
constructor-tagged option payload descent readback; the BEDC source is
$\mathsf{BHist}$ with a
$\mathsf{DescentCertificate}$; the carrier is tagged option histories; the
classifier is the transported tagged option classifier; the stability obligation
is visible branch preservation; the ledger is the absent/present tag with the
transported payload; the core theorem is this branch equivalence; exactness is
branch inversion; the standard bridge is none/some map readback; and the status
is $\mathsf{ProofTarget}$. Let $S,T:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC
history source carriers, let $\sim_S,\sim_T$ be source classifiers, let
$\delta:\mathsf{DescentCertificate}(\mathsf{BHist},\mathsf{BHist},\sim_S,\sim_T)$,
and let
$$
\rho_{\delta}:\forall a.\;S(a)\to T(\delta.\mathsf{map}(a)).
$$
For all histories $h,k$, every witness
$\mathsf{TaggedOptionMapRel}_{\delta}(S,T,\rho_{\delta};h,k)$ implies both
$$
\hsame(h,\emp)\Longleftrightarrow\hsame(k,\emp)
$$
and
$$
(\exists a:\mathsf{BHist}.\;S(a)\land\hsame(h,\Eone(a)))
\Longleftrightarrow
(\exists b:\mathsf{BHist}.\;T(b)\land\hsame(k,\Eone(b))).
$$
\end{theorem}
\begin{proof}
Split the map-relation witness into its visible branches.

In the absent branch, both endpoint presentations are $\emp$. Thus absentness is
preserved in either direction, and any present payload witness would identify an
empty presentation with a one-constructor presentation, contradicting
constructor no-confusion.

In the present branch, the exposed source payload $a$ supplies the left present
witness, while $\delta.\mathsf{map}(a)$ together with $\rho_{\delta}$ supplies
the right present witness. Either endpoint being absent would again identify
$\emp$ with a stored one-constructor presentation, so absentness agrees in both
directions.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.TaggedOptionMapRel\_visible\_branch\_equivalence}

\begin{theorem}[Tagged option map relation visible payload readback]
\label{thm:tagged-option-maprel-visible-payload-readback}
Let $S,T:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC history source carriers, let
$\sim_S,\sim_T$ be source classifiers, let
$\delta:\mathsf{DescentCertificate}(\mathsf{BHist},\mathsf{BHist},\sim_S,\sim_T)$,
and let
$$
\rho_{\delta}:\forall a.\;S(a)\to T(\delta.\mathsf{map}(a)).
$$
For histories $h,k,u,v$, assume
$$
\mathsf{TaggedOptionMapRel}_{\delta}(S,T,\rho_{\delta};h,k).
$$
If the visible source endpoint is presented by $u$ and the visible target
endpoint is presented by $v$,
$$
S(u)\land\hsame(h,\Eone(u))\land
T(v)\land\hsame(k,\Eone(v)),
$$
then there is an internal transported payload $a:\mathsf{BHist}$ such that
$$
S(a)\land T(\delta.\mathsf{map}(a))\land
\hsame(u,a)\land\hsame(v,\delta.\mathsf{map}(a)).
$$
\end{theorem}
\begin{proof}
Split the map-relation witness into its absent and present branches.

In the absent branch, the same source endpoint $h$ is presented both as $\emp$
and as $\Eone(u)$. Constructor no-confusion rules out this branch, so no visible
source payload can coexist with the absent map witness.

In the present branch, the map relation exposes a payload $a$ with $S(a)$,
$T(\delta.\mathsf{map}(a))$, $\hsame(h,\Eone(a))$, and
$\hsame(k,\Eone(\delta.\mathsf{map}(a)))$.

Invert the two one-constructor presentations of $h$ to obtain
$\hsame(u,a)$. Invert the two one-constructor presentations of $k$ to obtain
$\hsame(v,\delta.\mathsf{map}(a))$. The exposed carrier witnesses and these two
payload equalities package the required internal transported payload.
\end{proof}
