\begin{theorem}[Diagonal-limit representative cofinal-index source]
\label{thm:diagonal-limit-representative-cofinal-index-source}
For an accepted shared-terminal $\DiagonalLimitRepresentativeUp$ carrier, the cofinal-index source is the finite surface that reads the equations
$$
k=\mu(1/(n+1)),\qquad i=k+n+1
$$
through the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, $\CofinalModulusSealUp$, and $\RealUp$ rows used by the cofinal-terminal budget bridge. Thus the source of the selected window $w$, readback $r$, dyadic ledger $d$, finite-prefix budget rows, cofinal modulus rows, and terminal seal $e$ is visible before the terminal $\RealUp$ seal is consumed.
\end{theorem}
\begin{proof}
Project the root-index readiness package of \autoref{thm:diagonal-limit-representative-root-index-readiness-package}. It already exposes $\mu,n,k,i,w,r,d,e$ and forces the finite equations for $k$ and $i$ to appear on the root-index surface.

Next read the cofinal-terminal budget bridge of \autoref{def:diagonal-limit-representative-cofinal-terminal-budget-bridge}. Its packet attaches the finite-prefix rows and the cofinal modulus rows to the same terminal read, with $w,r,d,e$ identified with the matching cofinal window, readback, dyadic, and seal rows.

Finally apply the cofinal-budget seal totality theorem \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality}. It orders the entire route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, $\CofinalModulusSealUp$, and $\RealUp$, so the cofinal-index equations are sourced by the displayed rows rather than by a host equality, quotient stream, selected limit, hidden schedule, choice row, or ambient completeness principle.
\end{proof}

\begin{theorem}[Diagonal-limit representative cofinal-index budget lock]
\label{thm:diagonal-limit-representative-cofinal-index-budget-lock}
The finite-prefix budget rows and cofinal modulus rows of the cofinal-index source lock the selected window, readback, dyadic tolerance, and terminal-read tolerance before any terminal $\RealUp$ seal is read. In particular, a terminal consumer may read $e$ only after the representative rows, the finite-prefix budget rows $Q,B,W,D_F,R,S,E_F,H_F,C_F,P_F,N_F$, and the cofinal modulus rows $B_M,M_M,W_M,T_M,D_M,R_M,L_M,E_M,H_M,C_M,P_M,N_M$ have all been placed on the same finite $\BHist$ surface.
\end{theorem}
\begin{proof}
Begin with the cofinal-index source theorem \autoref{thm:diagonal-limit-representative-cofinal-index-source}. It places the finite equations and the selected representative rows on the same source route as the finite-prefix and cofinal modulus rows.

The bridge definition \autoref{def:diagonal-limit-representative-cofinal-terminal-budget-bridge} then supplies the concrete budget lock. It identifies $w$ with $T_M$, $r$ with $R_M$, $d$ with $D_M$, and $e$ with $E_M$, while keeping the finite-prefix selector and exhaustion rows visible before terminal consumption.

The totality theorem \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality} closes the tolerance route. Since every terminal seal read factors through the displayed StreamName, RegSeqRat, DyadicRatCore, finite-prefix budget, cofinal modulus, and Real rows, no consumer can read a terminal seal before those window, readback, dyadic, and tolerance coordinates are locked.
\end{proof}

\begin{theorem}[Diagonal-limit representative cofinal-index terminal readiness]
\label{thm:diagonal-limit-representative-cofinal-index-terminal-readiness}
The cofinal-index terminal readiness package for $\DiagonalLimitRepresentativeUp$ consists of the cofinal-index source \autoref{thm:diagonal-limit-representative-cofinal-index-source}, the cofinal-index budget lock \autoref{thm:diagonal-limit-representative-cofinal-index-budget-lock}, the root-index readiness package \autoref{thm:diagonal-limit-representative-root-index-readiness-package}, the cofinal-terminal budget bridge \autoref{def:diagonal-limit-representative-cofinal-terminal-budget-bridge}, the cofinal-budget seal totality theorem \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality}, and the terminal consumer nonescape theorem \autoref{thm:diagonal-limit-representative-terminal-consumer-cofinal-nonescape}. It is a finite readiness surface for Real-and-Completion consumers and carries no host equality, quotient stream equality, selected limit, hidden tail schedule, countable choice, ambient $\RealUp$ completeness, or Lean bridge claim.
\end{theorem}
\begin{proof}
The source theorem supplies the cofinal-index origin of the equations $k=\mu(1/(n+1))$ and $i=k+n+1$ across the named StreamName, RegSeqRat, DyadicRatCore, finite-prefix budget, cofinal modulus, and Real rows.

The budget-lock theorem supplies the ordering constraint. It makes the selected window, readback, dyadic ledger, finite-prefix rows, and cofinal modulus rows prerequisites for terminal seal consumption.

It remains to package the terminal boundary. The root-index readiness package gives the finite representative surface, the cofinal-terminal bridge gives the shared $\BHist$ packet, the cofinal-budget seal totality theorem gives the terminal route, and the terminal consumer nonescape theorem excludes every off-packet equality, selector, choice, completion, and bridge coordinate. Therefore the readiness package is exactly the finite cofinal-index surface stated above.
\end{proof}
