\begin{theorem}[Diagonal-limit representative hub dependency witness]
\label{thm:diagonal-limit-representative-hub-dependency-witness}
The hub-visible dependency witness for $\DiagonalLimitRepresentativeUp$ is the package consisting of the carrier and classifier of \autoref{def:diagonal-limit-representative-carrier} and \autoref{def:diagonal-limit-representative-classifier}, the shared-terminal carrier of \autoref{def:diagonal-limit-representative-shared-terminal-carrier}, the root-readiness triad of \autoref{thm:diagonal-limit-representative-root-readiness-triad}, the root-index readiness package of \autoref{thm:diagonal-limit-representative-root-index-readiness-package}, the cofinal-terminal budget bridge of \autoref{def:diagonal-limit-representative-cofinal-terminal-budget-bridge}, and the formal handoff boundary of \autoref{thm:diagonal-limit-representative-formal-handoff-boundary}. Its visible route factors through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, and $\RealUp$, with the cofinal terminal budget rows supplying the completion-facing budget source. It exposes no quotient streams, host real equality, hidden selectors, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
The carrier and classifier identify the accepted diagonal representative and its componentwise support rows. The shared-terminal carrier then attaches the finite-prefix budget rows to the same terminal read, so the hub package begins with one finite $\BHist$ surface rather than two unrelated surfaces.

The root-readiness triad supplies the mandatory display order for the modulus request, selected indices, selected window, readback, dyadic ledger, finite-prefix rows, and terminal $\RealUp$ seal. The root-index readiness package makes the equations for $k$ and $i$ visible before support rows are consumed, and it records that the named sibling certificates source each exposed row.

The cofinal-terminal budget bridge adds the completion-facing budget source without adding an analytic completion principle. Finally, the formal handoff boundary states that later Lean handoffs may encode only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and sibling rows. Hence the hub witness packages the existing obligations as a visible dependency route while preserving the quotient, host-equality, selector, choice, and completeness exclusions.
\end{proof}

\begin{theorem}[Diagonal-limit representative root-unblock consumer surface]
\label{thm:diagonal-limit-representative-root-unblock-consumer-surface}
Every Real-and-Completion consumer that reads the hub-visible $\DiagonalLimitRepresentativeUp$ dependency witness must consume the ordered surface
$$
\StreamNameUp \to \RegSeqRatUp \to \DyadicRatCoreUp \to \FinitePrefixLimitBudgetUp \to \RealUp
$$
through the accepted carrier rows of \autoref{def:diagonal-limit-representative-carrier}, the shared-terminal rows of \autoref{def:diagonal-limit-representative-shared-terminal-carrier}, the root-readiness route of \autoref{thm:diagonal-limit-representative-root-readiness-triad}, the root-index package of \autoref{thm:diagonal-limit-representative-root-index-readiness-package}, and the cofinal-budget seal totality theorem \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality}. No accepted consumer of this surface may replace the displayed route by quotient stream equality, host $\RealUp$ equality, a selected completed limit, a hidden selector, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the carrier and shared-terminal carrier. Together they display the representative rows $X,\mu,n,k,i,w,r,d,e,H,C,P,N$ and the finite-prefix rows $Q,B,W,D_F,R,S,E_F,H_F,C_F,P_F,N_F$ as one terminal packet.

Apply the root-readiness triad and root-index readiness package. They force the selected-index equations, selected window, readback, dyadic ledger, finite-prefix budget rows, and terminal Real seal to be visible before any downstream support row can be used.

Now use the cofinal-budget seal totality theorem. It routes the completion-facing seal through the StreamName, RegSeqRat, DyadicRatCore, finite-prefix budget, cofinal modulus, and Real surfaces. The formal handoff boundary then removes any off-packet quotient, host-equality, selected-limit, hidden-selector, choice, or ambient-completeness entrance. Thus the consumer surface is exactly the ordered finite route stated above.
\end{proof}

\begin{theorem}[Diagonal-limit representative L10 exit readiness package]
\label{thm:diagonal-limit-representative-l10-exit-readiness-package}
The L10 exit readiness package exported at the $\DiagonalLimitRepresentativeUp$ hub consists of the hub dependency witness of \autoref{thm:diagonal-limit-representative-hub-dependency-witness}, the root-unblock consumer surface of \autoref{thm:diagonal-limit-representative-root-unblock-consumer-surface}, the terminal pullback coverage theorem \autoref{thm:diagonal-limit-representative-terminal-pullback-coverage}, and the terminal consumer cofinal nonescape theorem \autoref{thm:diagonal-limit-representative-terminal-consumer-cofinal-nonescape}. This package is ready for Real and Completion consumers precisely because every exit row is already routed through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, and $\RealUp$, with no quotient streams, host real equality, hidden selectors, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
The hub dependency witness gathers the existing carrier, shared-terminal, root-readiness, root-index, cofinal-terminal, and formal-handoff obligations into one public package. The root-unblock consumer surface then states the exact order in which a Real-and-Completion consumer may read that package.

Terminal pullback coverage supplies the exit coverage: every accepted formal handoff pulls downstream consumption back to the finite representative and budget rows. Terminal consumer cofinal nonescape supplies the negative boundary: the cofinal-terminal budget bridge admits only the displayed representative, finite-prefix, cofinal modulus, and structural BEDC rows.

It remains to name the exported readiness. Since the positive route is the displayed finite path through StreamName, RegSeqRat, DyadicRatCore, finite-prefix budget, and Real surfaces, and since every quotient, host-equality, hidden-selector, choice, and ambient-completeness alternative is excluded by the cited boundaries, the hub exports a dependency-ready L10 exit package for the Real and Completion phases.
\end{proof}
