\begin{theorem}[Diagonal-limit representative four-object source exhaustion]
\label{thm:diagonal-limit-representative-four-object-source-exhaustion}
Every accepted completion-selector ledger for $\DiagonalLimitRepresentativeUp$ exposes exactly the four source rows needed by a Phase Real and Completion consumer: the $\DyadicRatCoreUp$ radius row, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity readback row, and the terminal $\RealUp$ seal row. These rows are read through the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ support already displayed by the ledger, with the sibling chapters \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert} supplying the cited source surfaces.
\end{theorem}
\begin{proof}
Start with the StreamName--RegSeqRat handoff of \autoref{thm:diagonal-limit-representative-streamname-regseqrat-handoff}. It orders every accepted route to the seal through the selected finite window $w$, the selected regular-rational readback $r$, the downstream dyadic ledger $d$, and the terminal Real seal $e$.

Now use the L10 completion root package of \autoref{thm:diagonal-limit-representative-l10-completion-root-package}. That package gathers the root-index, terminal cofinal extraction, Real-seal extraction, NameCert ledger, formal handoff boundary, and Real-completion consumer exactness rows into one finite completion-frontier handoff.

Finally apply completion handoff exhaustion, \autoref{thm:diagonal-limit-representative-completion-handoff-exhaustion}. It states that every Real-and-Completion consumer remains inside the displayed StreamName, RegSeqRat, DyadicRatCore, finite-prefix, cofinal-modulus, Real, and local support rows. Projecting the four requested source coordinates gives the listed DyadicRatCore radius, StreamName finite-window, RegSeqRat regularity, and Real seal rows.
\end{proof}

\begin{theorem}[Diagonal-limit representative Phase Real and Completion exit certificate]
\label{thm:diagonal-limit-representative-phase-real-completion-exit-certificate}
For every accepted completion-selector ledger for $\DiagonalLimitRepresentativeUp$, the four rows named in \autoref{thm:diagonal-limit-representative-four-object-source-exhaustion} form the Phase Real and Completion exit packet. The packet is a finite BEDC source certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$; it carries no quotient stream equality, no countable or dependent choice principle, no ambient completeness theorem, no trichotomy claim, and no open-cover compactness claim.
\end{theorem}
\begin{proof}
The four-object exhaustion theorem supplies the source coordinates and ties them to the four sibling chapters. Thus the packet has named BEDC sources for radius accounting, finite-window exposure, regularity readback, and terminal Real sealing.

The completion-selector ledger of \autoref{def:diagonal-limit-representative-completion-selector-ledger} records the same rows inside one finite $\BHist$ tuple with $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ support. It also states that host limits, quotient stream equality, selected completion points, choice rows, and ambient completeness fields are not ledger coordinates.

Use completion handoff exhaustion to close the certificate boundary. Since every consumer factors through the displayed finite rows, stronger analytic principles such as trichotomy or open-cover compactness cannot enter through this exit packet.
\end{proof}

\begin{theorem}[Diagonal-limit representative audit-clean consumer handoff]
\label{thm:diagonal-limit-representative-audit-clean-consumer-handoff}
Downstream Real-completion consumers may cite the Phase Real and Completion exit packet of \autoref{thm:diagonal-limit-representative-phase-real-completion-exit-certificate} as the finite BEDC source surface for $\DiagonalLimitRepresentativeUp$. Such a citation commits only to the displayed DyadicRatCore, StreamName, RegSeqRat, Real, and local support rows, and not to any off-packet completion principle or hidden selector.
\end{theorem}
\begin{proof}
Begin with the Phase Real and Completion exit certificate. It identifies the four named source rows as the whole exit packet and excludes quotient, choice, ambient completeness, trichotomy, and open-cover compactness claims.

Then apply the completion handoff exhaustion theorem. Any Real-and-Completion consumer of the accepted ledger factors through the displayed sibling surfaces and the finite local support rows, so citing the exit packet is sufficient for downstream source accounting.

The L10 completion root package supplies the public citation boundary. It gathers the relevant terminal extraction, Real-seal extraction, root-readiness, NameCert, formal handoff, and consumer exactness results without exporting a stronger completion object. Therefore the handoff is audit-clean as a finite BEDC source surface.
\end{proof}
