\begin{theorem}[Diagonal-limit representative phase-root window totality]
\label{thm:diagonal-limit-representative-phase-root-window-totality}
Every Phase Real and Completion root-window read accepted by $\DiagonalLimitRepresentativeUp$ is total on the finite packet
$$
(\mu,n,k,i,w,r,d,H,C,P,N)
$$
where $k=\mu(1/(n+1))$ and $i=k+n+1$. The rows $w,r,d$ are respectively the displayed $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ faces, while $H,C,P,N$ are the displayed $\BHist$, componentwise $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\DiagonalLimitRepresentativeUp}$ support rows. The terminal $\RealUp$ seal is reachable only after this packet is displayed, through the sibling chapters \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\begin{proof}
Start with the carrier and classifier of \autoref{def:diagonal-limit-representative-carrier} and \autoref{def:diagonal-limit-representative-classifier}. They expose only finite representative rows and compare them through the displayed support, so the root-window read has no coordinate outside $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ data.

Apply root-readiness exactness, the modulus-window-readback package, and the terminal-modulus scope lock, \autoref{thm:diagonal-limit-representative-root-readiness-exactness}, \autoref{thm:diagonal-limit-representative-modulus-window-readback-package}, and \autoref{thm:diagonal-limit-representative-terminal-modulus-scope-lock}. These results compute $k$ and $i$, display the selected window and readback, and bind the dyadic ledger to the same finite route.

Finally use the four-object source exhaustion theorem, \autoref{thm:diagonal-limit-representative-four-object-source-exhaustion}. It identifies the Real-and-Completion source inventory with the DyadicRatCore, StreamName, RegSeqRat, and Real rows. Hence every accepted phase-root window read is total exactly on the stated finite packet before the terminal Real seal is consumed.
\end{proof}

\begin{theorem}[Diagonal-limit representative phase-root readback factorization]
\label{thm:diagonal-limit-representative-phase-root-readback-factorization}
Every accepted Phase Real and Completion readback for $\DiagonalLimitRepresentativeUp$ factors through the ordered root-window route
$$
\StreamNameUp \to \RegSeqRatUp \to \DyadicRatCoreUp \to \RealUp
$$
carried by the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ rows. The factorization reads the selected finite window $w$ before the regular-rational readback $r$, reads the dyadic tolerance ledger $d$ before the terminal $\RealUp$ seal, and exports no quotient stream equality, host limit, selected completed point, choice row, or ambient completeness principle.
\end{theorem}
\begin{proof}
First read the StreamName--RegSeqRat handoff, \autoref{thm:diagonal-limit-representative-streamname-regseqrat-handoff}. It forces any accepted route toward the terminal seal to expose the selected $\StreamNameUp$ window before the selected $\RegSeqRatUp$ readback.

Next apply finite selector exhaustion and the cofinal-tail exactness lock, \autoref{thm:diagonal-limit-representative-finite-selector-exhaustion} and \autoref{thm:diagonal-limit-representative-cofinal-tail-exactness-lock}. These keep the selected readback attached to the displayed root indices and dyadic ledger rather than to a detached tail principle.

The terminal step is supplied by the Phase Real and Completion exit certificate, \autoref{thm:diagonal-limit-representative-phase-real-completion-exit-certificate}. Since that certificate has exactly the four named source rows and no stronger analytic coordinate, every accepted readback factors through the ordered root-window route stated above.
\end{proof}

\begin{theorem}[Diagonal-limit representative phase-root nonchoice boundary]
\label{thm:diagonal-limit-representative-phase-root-nonchoice-boundary}
The Phase Real and Completion root-window surface for $\DiagonalLimitRepresentativeUp$ is a nonchoice boundary. Its available data are precisely the displayed $\BHist$ rows, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, local $\NameCert_{\DiagonalLimitRepresentativeUp}$ naming, and the sibling $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces. It cannot be strengthened into quotient stream equality, host-limit selection, countable choice, a selected completed point, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the root NameCert obligations, \autoref{thm:diagonal-limit-representative-namecert-obligations} and \autoref{thm:diagonal-limit-representative-namecert-ledger}. They record carrier admission, classifier stability, provenance, and naming as finite obligations rather than as external equality or selection principles.

Use support-scope nonescape and Real-seal nonchoice export, \autoref{thm:diagonal-limit-representative-hsame-cont-scope} and \autoref{thm:diagonal-limit-representative-real-seal-nonchoice-export}. The support rows may transport and replay only the displayed packet, and the Real-facing seal cannot be replaced by host equality, quotient equality, a hidden selector, or choice data.

Finally read the objectwise audit threshold handoff, \autoref{thm:diagonal-limit-representative-objectwise-audit-threshold-handoff}. It leaves downstream consumers with only the four objectwise faces and local support. Therefore the phase-root window surface is exactly the stated nonchoice boundary.
\end{proof}

\begin{theorem}[Diagonal-limit representative phase-root NameCert exhaustion]
\label{thm:diagonal-limit-representative-phase-root-namecert-exhaustion}
The $\NameCert_{\DiagonalLimitRepresentativeUp}$ obligation for a Phase Real and Completion root-window read is exhausted by the carrier, classifier, root-window totality theorem, readback factorization theorem, and nonchoice boundary theorem. Equivalently, once the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, local $\NameCert$, and sibling $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows are present, no additional NameCert clause is available for quotient streams, host limits, choice, selected completion points, or ambient completeness.
\end{theorem}
\begin{proof}
The carrier and classifier supply the underlying admissible rows. The root-window totality theorem then records that every accepted phase-root read has a displayed finite packet before any terminal Real seal is read.

The readback factorization theorem supplies the ordered source route through StreamName, RegSeqRat, DyadicRatCore, and Real. Thus each consumer-visible readback coordinate is already attached to a named sibling source and to the local support rows.

The nonchoice boundary theorem closes the negative ledger. Since it removes quotient equality, host limits, choice rows, selected completed points, and ambient completeness from the surface, there is no remaining NameCert obligation outside the listed packet.
\end{proof}

\begin{theorem}[Diagonal-limit representative phase-root consumer handoff]
\label{thm:diagonal-limit-representative-phase-root-consumer-handoff}
Every Real-and-Completion consumer of the $\DiagonalLimitRepresentativeUp$ phase-root window receives exactly the finite handoff supplied by the phase-root NameCert exhaustion theorem. The handoff consists of the root-window totality packet, the readback factorization route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ support. It exports no quotient stream equality, host limit, choice row, selected completed point, ambient completeness principle, or standard bridge row.
\end{theorem}
\begin{proof}
First assemble the local surface from root-window totality and readback factorization. These two theorems provide the finite packet and its ordered sibling route, so the consumer has a concrete row to read for each source face.

Next apply phase-root NameCert exhaustion. It states that the displayed support rows and four sibling faces already cover the local NameCert obligation, with no additional completion or selection clause.

Finally compare with the phase-exit handoff lock, \autoref{thm:diagonal-limit-representative-phase-exit-handoff-lock}. That theorem identifies the Phase Real and Completion endpoint as a finite consumer handoff and refuses quotient streams, selected completed points, countable choice, host Real limits, and ambient completion principles. The consumer therefore receives exactly the finite phase-root window handoff and nothing stronger.
\end{proof}
