\begin{theorem}[Diagonal-limit representative root-index coverage]
\label{thm:diagonal-limit-representative-root-index-coverage}
For an accepted shared-terminal $\DiagonalLimitRepresentativeUp$ carrier, every root-index consumer of the diagonal representative must expose the finite equations
$$
k=\mu(1/(n+1)),\qquad i=k+n+1
$$
before it consumes the visible route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, and $\RealUp$. Concretely, the consumer reads the selected window $w$, regular-rational readback $r$, dyadic ledger $d$, finite-prefix rows $Q,B,W,D_F,R,S,E_F,H_F,C_F,P_F,N_F$, and terminal seal $e$ as one finite index surface; it receives no quotient-stream equality, host Real equality, hidden tail selector, countable-choice row, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:diagonal-limit-representative-carrier}. Its displayed rows already contain the modulus request $\mu,n$, the computed indices $k,i$, the selected $\StreamNameUp$ window $w$, the $\RegSeqRatUp$ readback $r$, the $\DyadicRatCoreUp$ ledger $d$, and the terminal $\RealUp$ seal $e$.

Attach the shared-terminal carrier of \autoref{def:diagonal-limit-representative-shared-terminal-carrier}. It places the finite-prefix budget rows $Q,B,W,D_F,R,S,E_F,H_F,C_F,P_F,N_F$ on the same terminal read, so the root-index consumer sees one ordered route rather than a detached budget.

Finally use the root-readiness triad \autoref{thm:diagonal-limit-representative-root-readiness-triad} and the readback-index scope \autoref{thm:diagonal-limit-representative-readback-index-scope}. They force the equations for $k$ and $i$ to be visible before support rows are consumed, while the shared-terminal route supplies the StreamName, RegSeqRat, DyadicRatCore, FinitePrefixLimitBudget, and Real surfaces.
\end{proof}

\begin{theorem}[Diagonal-limit representative root-index soundness]
\label{thm:diagonal-limit-representative-root-index-soundness}
The root-index surface of \autoref{thm:diagonal-limit-representative-root-index-coverage} is sound for the Real-and-Completion route. Each exposed row is sourced by the named sibling certificate: $w$ by $\StreamNameUp$, $r$ by $\RegSeqRatUp$, $d$ by $\DyadicRatCoreUp$, $Q,B,W,D_F,R,S,E_F,H_F,C_F,P_F,N_F$ by $\FinitePrefixLimitBudgetUp$, and $e$ by the terminal $\RealUp$ seal row. The finite equations $k=\mu(1/(n+1))$ and $i=k+n+1$ are the only index computations admitted by this surface.
\end{theorem}
\begin{proof}
First read the public exactness package \autoref{thm:diagonal-limit-representative-public-exactness-package}. It identifies the ordered public route over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FinitePrefixLimitBudgetUp$, and $\RealUp$ and lists the representative and finite-prefix rows that the route may expose.

Next apply the terminal-seal root unblock \autoref{thm:diagonal-limit-representative-terminal-seal-root-unblock}. It shows that the terminal seal is reached only through the displayed finite rows, so none of the sibling surfaces can be replaced by an off-packet equality, selector, choice datum, or completion principle.

The formal handoff boundary \autoref{thm:diagonal-limit-representative-formal-handoff-boundary} supplies the remaining boundary. A later handoff may encode the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and sibling rows, but it cannot import any stronger analytic object. Hence the root-index route is sourced exactly by the named sibling certificates and by the two finite index equations.
\end{proof}

\begin{theorem}[Diagonal-limit representative root-index readiness package]
\label{thm:diagonal-limit-representative-root-index-readiness-package}
The root-index readiness package for $\DiagonalLimitRepresentativeUp$ consists exactly of the coverage theorem \autoref{thm:diagonal-limit-representative-root-index-coverage}, the soundness theorem \autoref{thm:diagonal-limit-representative-root-index-soundness}, the root-readiness exactness theorem \autoref{thm:diagonal-limit-representative-root-readiness-exactness}, the shared-terminal route \autoref{thm:diagonal-limit-representative-shared-terminal-route}, and the formal handoff boundary \autoref{thm:diagonal-limit-representative-formal-handoff-boundary}. Downstream Real-and-Completion consumers may use this package as a finite root-index surface, but it does not assert Real completeness, host real equality, quotient stream equality, selected limits, hidden tail schedules, countable choice, or any Lean bridge check.
\end{theorem}
\begin{proof}
Coverage supplies the visible data: the modulus request, the two finite index equations, the selected window and readback, the dyadic ledger, the finite-prefix budget rows, and the terminal Real seal.

Soundness supplies the source of each row through the StreamName, RegSeqRat, DyadicRatCore, FinitePrefixLimitBudget, and Real certificates. The root-readiness exactness theorem then states that downstream Real-and-Completion consumers factor through this finite packet and no stronger support route.

It remains to package the result at the handoff boundary. The shared-terminal route keeps the representative and finite-prefix rows on one terminal surface, while the formal handoff boundary confines later formal work to the displayed BEDC rows. Therefore the readiness package is exactly the finite root-index surface described above, with all host, quotient, selector, choice, completion, and bridge claims outside its scope.
\end{proof}
