\begin{theorem}[Diagonal-limit representative root-window selector lock]
\label{thm:diagonal-limit-representative-root-window-selector-lock}
Every Phase Real and Completion root-window selector read of an accepted $\DiagonalLimitRepresentativeUp$ carrier factors through the displayed finite route
$$
(\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp,\RealUp,\BHist,\hsame,\Cont,\Pkg,\NameCert)
$$
already named by the chapter. Concretely, the read exposes the selected equations $k=\mu(1/(n+1))$ and $i=k+n+1$, the finite window $w$, regular-rational readback $r$, dyadic ledger $d$, terminal seal $e$, and support rows $H,C,P,N$ before any downstream consumer can use the selector. No selector read bypasses those rows through quotient stream equality, host $\RealUp$ equality, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier and classifier rows of \autoref{def:diagonal-limit-representative-carrier} and \autoref{def:diagonal-limit-representative-classifier}. They list exactly the selected index equations, window, readback, ledger, terminal seal, transport, continuation, provenance, and local naming rows available to an accepted carrier.

Next apply the phase-root window totality and readback factorization theorems, \autoref{thm:diagonal-limit-representative-phase-root-window-totality} and \autoref{thm:diagonal-limit-representative-phase-root-readback-factorization}. These force the consumer to read the selected $\StreamNameUp$ window before the $\RegSeqRatUp$ readback and the $\DyadicRatCoreUp$ ledger before the terminal $\RealUp$ seal.

Finally use the phase-root nonchoice boundary and NameCert exhaustion, \autoref{thm:diagonal-limit-representative-phase-root-nonchoice-boundary} and \autoref{thm:diagonal-limit-representative-phase-root-namecert-exhaustion}. They identify $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ as the whole support surface, so the forbidden quotient, host-equality, selected-limit, choice, and completeness data have no coordinate in the selector read.
\end{proof}

\begin{theorem}[Diagonal-limit representative cofinal-modulus route totality]
\label{thm:diagonal-limit-representative-cofinal-modulus-route-totality}
The cofinal modulus route consumed by $\DiagonalLimitRepresentativeUp$ is total only through the finite selected-index route, finite-window route, dyadic-readback route, and terminal Real-seal route already displayed by the packet. Its positive data are the selected equations $k=\mu(1/(n+1))$ and $i=k+n+1$, the $\StreamNameUp$ window row, the $\RegSeqRatUp$ readback row, the $\DyadicRatCoreUp$ ledger row, the cofinal budget rows, the terminal $\RealUp$ seal row, and the recorded $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ support. It contains no quotient stream, countable-choice row, host real equality, or ambient completeness field.
\end{theorem}
\begin{proof}
Begin with the cofinal-index source and budget lock, \autoref{thm:diagonal-limit-representative-cofinal-index-source} and \autoref{thm:diagonal-limit-representative-cofinal-index-budget-lock}. They attach the selected-index equations to the finite window, readback, dyadic ledger, cofinal budget, and terminal seal before a downstream consumer can read the route.

Now apply cofinal-budget seal totality, \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality}. It orders every terminal seal read through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, the finite-prefix budget, the cofinal modulus rows, and $\RealUp$.

It remains to close the negative boundary. The terminal consumer cofinal nonescape theorem and Real-completion consumer exactness, \autoref{thm:diagonal-limit-representative-terminal-consumer-cofinal-nonescape} and \autoref{thm:diagonal-limit-representative-real-completion-consumer-exactness}, keep all transport inside the displayed structural rows and exclude quotient streams, countable choice, host real equality, and ambient completeness from the total route.
\end{proof}

\begin{theorem}[Diagonal-limit representative phase-exit unblock package]
\label{thm:diagonal-limit-representative-phase-exit-unblock-package}
The root-unblock package for $\DiagonalLimitRepresentativeUp$ consumed by the Phase Real and Completion exit route is the package consisting of the root-window selector lock of \autoref{thm:diagonal-limit-representative-root-window-selector-lock}, the cofinal-modulus route totality theorem of \autoref{thm:diagonal-limit-representative-cofinal-modulus-route-totality}, Real-completion consumer exactness \autoref{thm:diagonal-limit-representative-real-completion-consumer-exactness}, the formal handoff boundary \autoref{thm:diagonal-limit-representative-formal-handoff-boundary}, and the Phase Real and Completion exit certificate \autoref{thm:diagonal-limit-representative-phase-real-completion-exit-certificate}. A downstream exit consumer may cite this package only as a finite route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\DiagonalLimitRepresentativeUp}$ support; it cannot infer Real completeness, host equality, quotient streams, selected completed limits, countable choice, or bridge-checked status.
\end{theorem}
\begin{proof}
Assemble the two local obligations first. The root-window selector lock supplies the selected-index, finite-window, readback, dyadic ledger, terminal seal, and support rows, while the cofinal-modulus route totality theorem attaches the cofinal budget route to the same finite terminal read.

Next add Real-completion consumer exactness and the formal handoff boundary. Exactness confines every downstream consumer to the displayed StreamName, RegSeqRat, DyadicRatCore, cofinal budget, Real, and support rows. The handoff boundary states that later formal work may encode those rows without importing quotient equality, host equality, selected limits, choice, or ambient completeness.

Finally cite the Phase Real and Completion exit certificate. It identifies the consumer-facing source inventory with $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Therefore the exit route receives exactly the finite root-unblock package stated above and no stronger analytic or bridge claim.
\end{proof}
