\begin{theorem}[Diagonal-limit representative root carrier window]
\label{thm:diagonal-limit-representative-root-carrier-window}
For every accepted $\DiagonalLimitRepresentativeUp$ carrier
$$
D=(X,\mu,n,k,i,w,r,d,e,H,C,P,N),
$$
the root carrier window exposes, as one finite $\BHist$ packet, the regular-Cauchy family $X$, the modulus row $\mu$, the selected equations $k=\mu(1/(n+1))$ and $i=k+n+1$, the $\StreamNameUp$ window $w$, the $\RegSeqRatUp$ readback $r$, the $\DyadicRatCoreUp$ ledger $d$, the terminal $\RealUp$ seal $e$, the transport row $H$, the continuation row $C$, the provenance row $P$, and the local $\NameCert_{\DiagonalLimitRepresentativeUp}$ row $N$. The window contains no quotient stream equality, host limit, choice row, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:diagonal-limit-representative-carrier}. Its displayed tuple is exactly $X,\mu,n,k,i,w,r,d,e,H,C,P,N$, with the two selected-index equations and the four support rows already present in the finite packet.

Read the sibling route named in the chapter opening. The window coordinate is sourced by $\StreamNameUp$, the readback coordinate by $\RegSeqRatUp$, the arithmetic ledger by $\DyadicRatCoreUp$, and the terminal seal by $\RealUp$.

The carrier definition also states the negative boundary: no host real, quotient stream equality, hidden tail selector, countable choice row, or ambient completeness field is exported. Therefore the accepted root carrier window is precisely the finite $\BHist$ packet above.
\end{proof}

\begin{theorem}[Diagonal-limit representative classifier transport]
\label{thm:diagonal-limit-representative-classifier-transport}
If two accepted $\DiagonalLimitRepresentativeUp$ carriers are related by the classifier of \autoref{def:diagonal-limit-representative-classifier}, then the selected-index equation, $\StreamNameUp$ window row, $\RegSeqRatUp$ readback row, $\DyadicRatCoreUp$ ledger row, and terminal $\RealUp$ seal row transport only through the displayed $H$ and $C$ rows. In particular, classifier transport preserves the root-readiness route of \autoref{thm:diagonal-limit-representative-root-readiness-triad} and the root-index readiness package of \autoref{thm:diagonal-limit-representative-root-index-readiness-package} without adding an off-packet selector, quotient equality, host limit, choice row, or ambient completeness field.
\end{theorem}
\begin{proof}
Start with the classifier definition. It relates accepted carriers only by componentwise recorded $\hsame$ comparisons and displayed $\Cont$ routes over the selected indices, window, readback, dyadic ledger, terminal seal, package row, and local naming row.

Apply the root-readiness triad. It requires every Real-and-Completion consumer to expose the modulus request, selected indices, window, readback, dyadic ledger, finite-prefix budget rows, and terminal seal before any support row is consumed.

Now apply the root-index readiness package. It makes the equations for $k$ and $i$ and the sibling sources for $w,r,d,e$ part of the finite root-index surface. Since the classifier offers no support coordinate outside $H$ and $C$, transport of those rows can only be the displayed componentwise transport and replay.
\end{proof}

\begin{theorem}[Diagonal-limit representative NameCert ledger exhaustion]
\label{thm:diagonal-limit-representative-namecert-ledger}
The local $\NameCert_{\DiagonalLimitRepresentativeUp}$ ledger for the root-unblock surface is exhausted by the carrier of \autoref{def:diagonal-limit-representative-carrier}, the classifier of \autoref{def:diagonal-limit-representative-classifier}, the root-readiness route of \autoref{thm:diagonal-limit-representative-root-readiness-triad}, the cofinal-terminal budget bridge and seal totality of \autoref{thm:diagonal-limit-representative-cofinal-budget-seal-totality}, the formal handoff boundary of \autoref{thm:diagonal-limit-representative-formal-handoff-boundary}, and the hub dependency witness of \autoref{thm:diagonal-limit-representative-hub-dependency-witness}. No further ledger row is available to a Real-and-Completion consumer.
\end{theorem}
\begin{proof}
First read the carrier and classifier. They provide the accepted tuple, its componentwise comparison rule, and the local naming row $N$.

Next use the hub dependency witness. It packages the carrier, classifier, shared-terminal rows, root-readiness route, root-index package, cofinal-terminal bridge, and formal handoff boundary as the hub-visible dependency route.

Finally apply cofinal-budget seal totality and the formal handoff boundary. The seal totality theorem routes every terminal seal read through the displayed StreamName, RegSeqRat, DyadicRatCore, finite-prefix budget, cofinal modulus, and Real surfaces, while the handoff boundary prevents any stronger analytic object from entering. Hence the local NameCert ledger is exhausted by the listed rows and obligations.
\end{proof}

\begin{theorem}[Diagonal-limit representative index unary closure]
\label{thm:diagonal-limit-representative-index-unary-closure}
For every accepted $\DiagonalLimitRepresentativeUp$ carrier
$$
D=(X,\mu,n,k,i,w,r,d,e,H,C,P,N),
$$
the selected family row, modulus row, precision request, selected family index, selected readback index, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, terminal $\RealUp$ seal, and local $\NameCert_{\DiagonalLimitRepresentativeUp}$ row are $\mathsf{UnaryHistory}$ rows. Moreover, any derived route read produced by the displayed $\Cont$ closures
$$
\Cont(\mu,n,k),\qquad \Cont(w,r,i),\qquad \Cont(d,e,H)
$$
remains a $\mathsf{UnaryHistory}$ row. These are precisely the unary rows exposed by the carrier of \autoref{def:diagonal-limit-representative-carrier} and the NameCert obligations of \autoref{thm:diagonal-limit-representative-namecert-obligations}; no quotient stream equality, host limit, choice row, or ambient $\RealUp$ completeness row can serve as a replacement index source.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:diagonal-limit-representative-carrier}. It displays $X,\mu,n,k,i,w,r,d,e$ and the local naming row $N$ as finite $\BHist$ coordinates of the accepted representative packet.

Apply the NameCert obligations of \autoref{thm:diagonal-limit-representative-namecert-obligations}. Their Lean touchpoint, $\mathsf{DiagonalLimitRepresentativeNameCertObligations}$, records the same carrier rows as $\mathsf{UnaryHistory}$ data and closes the derived reads by the three displayed $\Cont$ routes.

The sibling route supplies the sources of those rows: $\StreamNameUp$ exposes $w$, $\RegSeqRatUp$ exposes $r$, $\DyadicRatCoreUp$ exposes $d$, and $\RealUp$ exposes $e$. Since every derived read is obtained by continuation from already displayed unary rows, the root index surface remains a $\BHist$ obligation surface rather than an analytic completion claim.
\end{proof}

\begin{theorem}[Diagonal-limit representative continuation route closure]
\label{thm:diagonal-limit-representative-cont-route-closure}
The accepted $\Cont$ routes for the root-unblock surface of an accepted $\DiagonalLimitRepresentativeUp$ packet are exactly the modulus-request route, the window-readback route, and the ledger-seal route:
$$
\Cont(\mu,n,k),\qquad \Cont(w,r,i),\qquad \Cont(d,e,H).
$$
The first route reads the selected family index from the displayed modulus request, the second route reads the selected readback index from the $\StreamNameUp$ window and $\RegSeqRatUp$ readback, and the third route carries the $\DyadicRatCoreUp$ ledger into the terminal $\RealUp$ seal. No accepted root consumer has a fourth continuation route through a hidden selector, quotient stream equality, host limit, choice row, or ambient completeness field.
\end{theorem}
\begin{proof}
Read the carrier and classifier of \autoref{def:diagonal-limit-representative-carrier} and \autoref{def:diagonal-limit-representative-classifier}. The carrier lists the continuation support row $C$, while the classifier permits replay only along the recorded componentwise $\Cont$ routes for the selected indices, window, readback, ledger, and seal.

Use \autoref{thm:diagonal-limit-representative-namecert-obligations}. The obligation theorem exposes exactly the three continuation closures named in the statement: modulus with request, window with readback, and ledger with terminal seal.

Finally follow the sibling route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$. That route accounts for every public read needed by a Real-and-Completion consumer, and the carrier contains no coordinate from which an additional accepted continuation could be sourced.
\end{proof}

\begin{theorem}[Diagonal-limit representative package and NameCert source closure]
\label{thm:diagonal-limit-representative-pkg-namecert-source-closure}
For every accepted $\DiagonalLimitRepresentativeUp$ carrier, the local package row $P$ and local naming row $N$ source the representative packet through the finite $\Pkg$ and $\NameCert_{\DiagonalLimitRepresentativeUp}$ surface of \autoref{def:diagonal-limit-representative-carrier}. The source surface is the displayed route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$, together with the carrier, classifier, and NameCert obligations of \autoref{thm:diagonal-limit-representative-namecert-obligations}. It does not source quotient stream equality, a host limit, a hidden choice selector, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the carrier. The rows $P$ and $N$ occur only as package provenance and local name for the displayed packet $D=(X,\mu,n,k,i,w,r,d,e,H,C,P,N)$.

Apply the NameCert obligations. They bind the local $\Pkg$ signature and $\NameCert_{\DiagonalLimitRepresentativeUp}$ row to the same unary rows and continuation closures used by the index and terminal routes.

The sibling route then identifies the packet source: $\StreamNameUp$ supplies the selected window, $\RegSeqRatUp$ supplies the readback, $\DyadicRatCoreUp$ supplies the ledger, and $\RealUp$ supplies the seal row. Because the source is exhausted by those finite rows plus $P$ and $N$, the local package cannot add quotient, host-limit, choice, or ambient-completeness data.
\end{proof}
