\begin{theorem}[CriticalLineWitness cross-lattice route]
\label{thm:criticallinewitness-cross-lattice-route}
Every accepted $\CriticalLineWitnessUp$ finite witness route consumed by \autoref{ch:concrete-instances-criticalstripbarrier-namecert} or \autoref{ch:concrete-instances-riemannzerocountledger-namecert} must expose the same displayed zeta-zero source row, strip-window row, real-part classifier row, modulus ledger row, and refusal ledger row before either downstream chapter reads the witness as a barrier or a zero-counting input. The route is therefore a finite BEDC handoff through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, not a host analytic assertion about zeros outside the displayed ledgers.
\end{theorem}
\begin{proof}
Project the $\CriticalLineWitnessUp$ carrier rows used by the hub siblings. The zeta-zero row supplies the source event, the strip row bounds the critical-window read, the real-part row records the line classifier, and the modulus row keeps the quantitative witness visible to consumers.

For \autoref{ch:concrete-instances-criticalstripbarrier-namecert}, the refusal ledger is the row that prevents a barrier consumer from replacing the displayed witness by an ambient strip theorem. For \autoref{ch:concrete-instances-riemannzerocountledger-namecert}, the same refusal ledger prevents a zero-counting consumer from reading an undisplayed counting formula.

The structural rows $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ transport and name exactly this finite route. Hence both downstream consumers receive the zeta-zero, strip, real-part, modulus, and refusal data before any barrier or counting use is available.
\end{proof}
