\begin{theorem}[CriticalLineWitness fixed-strip window carrier]
\label{thm:critical-line-witness-fixed-strip-window-carrier}
For an accepted $\CriticalLineWitnessUp$ packet, the fixed critical-strip window carrier is a finite $\BHist$ packet over the zero-strip source rows, rational modulus rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\CriticalLineWitnessUp}$ rows. Its visible surface is the fixed-strip tuple
$$
Z,S,M,R,Q,H,C,P,N,
$$
where $Z$ supplies the zero-strip source row, $S$ supplies the fixed critical-strip window, $M,R,Q$ supply the depth, real-part, and rational comparison ledgers, and $H,C,P,N$ supply transport, replay, provenance, and local naming.

The carrier has no coordinate for analytic continuation, a zero-producing search, host zero equality, quotient presentation, ambient completeness, or a proof of $\mathsf{RH}$.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_fixed\_strip\_window\_surface}
\begin{proof}
Start from the fixed-strip source tuple. It lists the zero row, strip row, depth row, real-part row, rational comparison row, transport, continuation, provenance, and local naming row as the whole fixed-strip source packet.

Apply fixed-strip source totality. Every fixed critical-strip source read is total on those displayed rows and on the finite observation window carried by the same $\BHist$ packet.

Finally use zero-route nonescape. Since the accepted route has no coordinate beyond $Z,S,M,R,Q,H,C,P,N$, analytic continuation, zero search, host equality, quotient presentation, ambient completeness, and $\mathsf{RH}$ proof data cannot be read from the carrier.
\end{proof}

\begin{theorem}[CriticalLineWitness fixed-strip modulus ledger]
\label{thm:critical-line-witness-fixed-strip-modulus-ledger}
For an accepted $\CriticalLineWitnessUp$ fixed-strip window carrier, every modulus comparison is exhausted by the displayed rational-modulus and zero-strip rows
$$
Z,S,M,R,Q,H,C,P,N.
$$
The comparison may read the supplied zero-strip source, fixed critical-strip window, depth row, real-part row, rational comparison ledger, componentwise transport, continuation replay, package provenance, and local naming row. It cannot import analytic continuation, zero-free-strip evidence, a global zero classifier, a host numeric oracle, quotient equality, ambient completeness, or a global $\mathsf{RH}$ assertion.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_fixed\_strip\_modulus\_ledger}
\begin{proof}
Begin with the fixed-strip window carrier above. It places every modulus-facing read on the same finite source and rational-comparison packet.

Use modulus refusal ledger exhaustion. The zero-strip/source modulus request is routed through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface, so the modulus comparison remains a ledger row rather than an analytic theorem.

Now apply RH-boundary nonescape through the fixed-strip source totality results. The downstream boundary receives only the displayed source and modulus rows, so analytic continuation, zero-free-strip evidence, global classifiers, host numeric oracles, quotient equality, ambient completeness, and global $\mathsf{RH}$ assertions are not exported.
\end{proof}

\begin{theorem}[CriticalLineWitness fixed-strip RH refusal]
\label{thm:critical-line-witness-fixed-strip-rh-refusal}
Every downstream $\mathsf{RH}$-facing consumer of an accepted $\CriticalLineWitnessUp$ fixed-strip window carrier receives only the displayed refusal ledger and the fixed-strip source window
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer may use the zero-strip source, fixed critical-strip window, rational modulus comparison, componentwise transport, continuation replay, package provenance, and local naming rows. It receives no proof of zero exclusion, no analytic-continuation theorem, no global zero classifier, no host zero-location certificate, no quotient presentation, and no ambient-completeness witness.
\end{theorem}
\begin{proof}
First read the downstream surface through the fixed-strip modulus ledger. It confines the $\mathsf{RH}$-facing request to the displayed zero-strip source, fixed-strip window, modulus comparison, and structural rows.

Next apply the RH-boundary NameCert handoff. The local $\NameCert_{\CriticalLineWitnessUp}$ handoff names the same fixed-strip source and modulus refusal ledger, not an analytic certificate.

Finally use the RH consumer boundary. The consumer receives only the finite BEDC witness boundary, so zero exclusion, analytic continuation, global zero classification, host zero-location certificates, quotient presentations, ambient completeness, and a proof of $\mathsf{RH}$ remain outside the accepted packet.
\end{proof}
