\begin{theorem}[Critical-line witness RH-refusal readback totality]
\label{thm:critical-line-witness-rh-refusal-readback-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every $\mathsf{RH}$-refusal readback of $W$ factors through the displayed zero-strip, modulus, and source rows
$$
Z,S,M,R,Q,H,C,P,N.
$$
The readback may cite the zero-strip/source totality of \autoref{thm:critical-line-witness-zero-strip-source-totality}, the modulus-depth ledger of \autoref{thm:critical-line-witness-modulus-depth-ledger}, and the RH-interface carrier of \autoref{thm:critical-line-witness-rh-interface-carrier}, but it exports only a finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ refusal row.
\end{theorem}
\begin{proof}
Project the accepted packet to its displayed zero, strip, modulus, real-part, rational-comparison, transport, route, provenance, and naming rows. These are exactly the coordinates available to a refusal readback.

Use \autoref{thm:critical-line-witness-zero-strip-source-totality} for the $Z,S,H,C,P,N$ side and \autoref{thm:critical-line-witness-modulus-depth-ledger} for the $M,R,Q,H,C,P,N$ side. The two routes share the same structural rows, so the readback remains one finite packet route.

Finally apply the RH-interface carrier and the existing refusal ledger. Since the packet has no coordinate for an $\mathsf{RH}$ theorem, analytic continuation theorem, host zero classifier, quotient representative, host equality, or ambient completeness principle, the refusal readback is exhausted by the displayed rows.
\end{proof}

\begin{theorem}[Critical-line witness zeta dependency lock]
\label{thm:critical-line-witness-zeta-dependency-lock}
Before any $\CriticalLineWitnessUp$ packet is exported as a critical-line witness, its dependency rows for $\ZetaContinuationWitnessUp$, $\ZetaZerosUp$, $\RatUp$, and $\RealUp$ are locked into the same finite route $Z,S,M,R,Q,H,C,P,N$. The continuation source is read only as a finite boundary surface, the zero row is read only through $Z$, the rational comparison ledger is read only through $Q$, and the real-part row is read only through $R$.
\end{theorem}
\begin{proof}
Start with the zeta dependency lattice of \autoref{thm:critical-line-witness-zeta-link}. It forces zero-strip and critical-line reads to consume the zeta-zero and RH-boundary surfaces before the modulus witness is public.

Next use \autoref{thm:critical-line-witness-zeta-dependency-readback} and \autoref{thm:critical-line-witness-downstream-source-package}. These theorems identify every zeta-facing readback with the supplied zero row, critical-strip row, modulus row, real-part row, rational-comparison row, and local structural rows.

The $\RatUp$ and $\RealUp$ sources are therefore not late imports. They are the displayed rows $Q$ and $R$ already bound to the accepted packet, while $\ZetaContinuationWitnessUp$ and $\ZetaZerosUp$ remain provenance and source surfaces consumed before export.
\end{proof}

\begin{theorem}[Critical-line witness downstream counter-surface]
\label{thm:critical-line-witness-downstream-counter-surface}
Every downstream counter-surface consumer of an accepted $\CriticalLineWitnessUp$ packet receives only the finite $\BHist$ refusal ledger over $Z,S,M,R,Q,H,C,P,N$. The consumer may inspect the supplied zero-strip source, modulus window, real-part row, rational comparison row, transport row, continuation row, provenance row, and local $\NameCert$ row, but it receives no proof or refutation of $\mathsf{RH}$, no analytic continuation theorem, and no host zero classifier.
\end{theorem}
\begin{proof}
Project the downstream read through \autoref{thm:critical-line-witness-root-refusal-downstream-gate}. That gate already restricts RH-facing consumers to the finite refusal package over the accepted packet.

Apply the RH-refusal readback totality theorem above. It identifies every such readback with the zero-strip, modulus, source, transport, route, provenance, and naming rows of $W$.

The non-export clauses in \autoref{thm:critical-line-witness-rh-boundary-refusal} and \autoref{thm:critical-line-witness-rh-interface-carrier} remove proof content, analytic continuation, and host zero classification from the consumer surface. Hence downstream consumers receive a finite counter-surface ledger and nothing stronger.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_downstream\_counter\_surface}
