\begin{theorem}[Critical-line witness source normalization lock]
\label{thm:critical-line-witness-source-normalization-lock}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Before a root or downstream $\mathsf{RH}$-boundary consumer reads any modulus, comparison, or refusal data, the supplied zero row $Z$ and critical-strip row $S$ are normalized as the source side of the same finite packet over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CriticalLineWitnessUp}$. The source lock uses only the supplied zero row, critical-strip row, Nat depth row, Rat comparison ledger, Real-part row, $H,C,P,N$, and the existing root source triad.
\end{theorem}
\begin{proof}
Project the accepted packet $W$. The carrier exposes $Z,S,M,R,Q,H,C,P,N$ and has no coordinate for a global zero classifier, analytic-continuation theorem, host equality, quotient representative, or ambient completeness principle.

Apply the root source triad \autoref{thm:critical-line-witness-root-source-triad} and the Lean-facing carrier root source triad. They identify the supplied zero row, the critical-strip row, and the source-facing comparison route as finite packet rows under the same transport, continuation, package, and local naming surface.

The modulus and comparison rows are therefore read only after $Z$ and $S$ have been exposed. Since the source side is locked before downstream inspection, an $\mathsf{RH}$-boundary consumer receives a source-normalized packet rather than a zero search or analytic source theorem.
\end{proof}

\begin{theorem}[Critical-line witness modulus ledger totality]
\label{thm:critical-line-witness-modulus-ledger-totality}
For every accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$ whose source side is locked as in \autoref{thm:critical-line-witness-source-normalization-lock}, every modulus, Nat-depth, Rat-comparison, and Real-part read is total through the displayed ledger $M,R,Q,H,C,P,N$ while retaining $Z$ and $S$ as the supplied zero-strip source rows. The ledger exports no hidden numeric oracle, host zero equality, quotient representative, analytic-continuation certificate, or ambient completeness row.
\end{theorem}
\begin{proof}
Begin with the source-normalization lock. It places the supplied zero and critical-strip rows upstream of every modulus-facing read.

Apply the root comparison ledger \autoref{thm:critical-line-witness-root-comparison-ledger} together with the root modulus ledger \autoref{thm:critical-line-witness-root-modulus-ledger}. These rows route Nat depth through $M$, Real-part data through $R$, and Rat comparison through $Q$, all under $H,C,P,N$.

Finally use the modulus-refusal scope already carried by the root packet. Because the ledger is finite and row-exact, every modulus request is answered by $M,R,Q,H,C,P,N$ and cannot leave the packet for host equality, quotient data, analytic continuation, or ambient completeness.
\end{proof}

\begin{theorem}[Critical-line witness RH-boundary refusal exhaustion]
\label{thm:critical-line-witness-rh-boundary-refusal-exhaustion}
Every $\mathsf{RH}$-boundary consumer of an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$ is exhausted by the locked source side $Z,S$, the total modulus ledger $M,R,Q$, and the structural rows $H,C,P,N$. The consumer may cite a supplied zero row, critical-strip row, Nat depth, Rat comparison ledger, Real-part row, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data, but it receives no $\mathsf{RH}$ proof, zero search, global zero classifier, analytic-continuation theorem, host equality, quotient stream, or ambient completeness datum.
\end{theorem}
\begin{proof}
Use \autoref{thm:critical-line-witness-source-normalization-lock} for the source side and \autoref{thm:critical-line-witness-modulus-ledger-totality} for the comparison side. Together they expose exactly the finite rows $Z,S,M,R,Q,H,C,P,N$.

Apply the RH-refusal ledger completeness theorem \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness} and the RH-boundary refusal totality row \autoref{thm:critical-line-witness-rh-boundary-refusal-totality}. These existing rows classify requests for proof content, zero search, analytic continuation, quotient data, host equality, and ambient completeness as refusal-side requests.

Thus the downstream boundary is exhausted by the packet itself. It remains a finite BEDC witness surface for supplied zero-strip and modulus data, not an analytic certificate and not a proof of $\mathsf{RH}$.
\end{proof}
