\begin{theorem}[Critical-line witness strip-depth readback totality]
\label{thm:critical-line-witness-strip-depth-readback-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every strip-depth read that starts from the supplied zero row $Z$, the fixed critical-strip row $S$, or a bounded depth request in $M$ routes through the finite rows
$$
Z,S,M,R,Q,H,C,P,N.
$$
The read may expose the supplied $\ZetaZerosUp$ row, the $\CritStripUp$ boundary, the $\NatUp$ depth budget, the $\RealUp$ real-part row, the $\RatUp$ comparison ledger, and the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, but no other strip-depth source.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:critical-line-witness-carrier}. The rows $Z,S,M,R,Q,H,C,P,N$ are the displayed coordinates of the same finite $\BHist$ packet, so a strip-depth consumer has no carrier coordinate outside that tuple.

Use \autoref{thm:critical-line-witness-zero-source-totality}, \autoref{thm:critical-line-witness-root-unblock-modulus-ledger}, and \autoref{thm:criticallinewitness-rational-height-window}. They route supplied zero reads, fixed-strip reads, and bounded depth requests through $Z,S,M$ before the real and rational comparison rows $R,Q$ are exposed.

Finally apply \autoref{thm:critical-line-witness-ledger-nonescape}. The transport, continuation, package, and local naming rows $H,C,P,N$ exhaust the remaining public readback surface, so every strip-depth read is confined to the displayed route.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_strip\_depth\_readback\_totality}

\begin{theorem}[Critical-line witness rational comparison ledger totality]
\label{thm:critical-line-witness-rational-comparison-ledger-totality}
For every accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, each rational comparison read is exhausted by the $\RealUp$ row $R$ and the $\RatUp$ ledger row $Q$, together with the local transport, continuation, package, and naming rows $H,C,P,N$. Such a read cannot import analytic-continuation data, a host zero theorem, a selected quotient representative, or proof data for $\mathsf{RH}$.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_rational\_comparison\_ledger\_totality}
\begin{proof}
Begin with the rational comparison surface. By \autoref{thm:critical-line-witness-root-comparison-ledger} and \autoref{thm:critical-line-witness-rat-comparison-ledger-exactness}, the only rows that compare the real-part and rational boundary data are $R$ and $Q$.

The depth source remains finite by \autoref{thm:critical-line-witness-strip-depth-readback-totality}. Thus the comparison read first consumes $Z,S,M$ as source and depth data, then reads $R,Q$ as the comparison ledger inside the same packet.

The refusal boundary follows from \autoref{thm:critical-line-witness-ledger-nonescape} and \autoref{thm:criticallinewitness-critical-strip-ledger}. Analytic continuation, host zero theorems, quotient representatives, and $\mathsf{RH}$ proof data have no coordinate in $W$, so the rational comparison ledger is total exactly at $R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness RH refusal ledger exactness]
\label{thm:critical-line-witness-rh-refusal-ledger-exactness}
Every $\mathsf{RH}$-facing consumer of an accepted $\CriticalLineWitnessUp$ packet receives only the finite refusal boundary carried by
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer may read the supplied zero row, fixed strip row, bounded depth row, real-part row, rational comparison row, transport row, continuation row, package row, and local naming row. It receives no proof of $\mathsf{RH}$, zero generator, quotient representative, host equality row, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the consumer route to the displayed carrier. The $\mathsf{RH}$-facing surface is still a read of the same finite packet $W=(Z,S,M,R,Q,H,C,P,N)$, not a separate analytic object.

Apply \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}, \autoref{thm:critical-line-witness-root-refusal-route}, and \autoref{thm:critical-line-witness-rational-comparison-ledger-totality}. These rows expose only the supplied zero, strip, depth, real, rational, transport, continuation, provenance, and naming data before the refusal boundary is reached.

The excluded objects would require coordinates for an $\mathsf{RH}$ theorem, a zero-producing generator, quotient representatives, host equality, or ambient completeness. Since none is present in the accepted packet, the refusal ledger is exact for every downstream $\mathsf{RH}$-facing consumer.
\end{proof}
