\begin{theorem}[Critical-line witness root finite-budget source totality]
\label{thm:critical-line-witness-root-finite-budget-source-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Every root finite-budget source read of $W$ is total on the displayed zero-strip
source rows, rational modulus and comparison ledger, transport, continuation,
package, and local naming surface
$$
Z,S,M,R,Q,H,C,P,N.
$$
The source read may expose the supplied $\ZetaZerosUp$ row, the
$\CritStripUp$ strip row, the $\NatUp$ depth row, the $\RealUp$ real-part row,
the $\RatUp$ comparison ledger, and the $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ rows. It exposes no $\mathsf{RH}$ proof, analytic continuation,
host zero classifier, quotient representative, host equality, or ambient
completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_finite\_budget\_source\_totality}
\begin{proof}
Start with the carrier route exactness and root source triad,
\autoref{thm:critical-line-witness-carrier-route-exactness} and
\autoref{thm:critical-line-witness-root-source-triad}. They place the supplied
zero row, critical-strip row, and rational comparison ledger inside the same
finite carrier.

Next apply the modulus ledger entry and root modulus-window totality,
\autoref{thm:critical-line-witness-modulus-ledger-entry} and
\autoref{thm:critical-line-witness-root-modulus-window-totality}. These rows
make $M,R,Q,H,C,P,N$ the whole depth and rational-comparison route available to
a root consumer.

Finally use the supplied zero-strip transport lock and RH-refusal ledger
completeness. The structural rows $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
carry the source and modulus faces together, while the refusal ledger removes
analytic continuation, host classifiers, quotient representatives, host
equality, ambient completeness, and any proof of $\mathsf{RH}$.
\end{proof}

\begin{theorem}[Critical-line witness root finite-budget ledger stability]
\label{thm:critical-line-witness-root-finite-budget-ledger-stability}
For an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, replacing a root finite-budget presentation by another
presentation with the same displayed $Z,S,M,R,Q$ rows preserves the rational
modulus ledger exactly through the same $\hsame/\Cont/\Pkg/\NameCert$ transport
surface. No stable ledger comparison may introduce a hidden modulus source,
analytic-continuation certificate, quotient representative, host equality, or
ambient completeness row.
\end{theorem}
\begin{proof}
First read the finite-budget source totality just established. It fixes the
available source and comparison rows at $Z,S,M,R,Q,H,C,P,N$, so a second
presentation has no additional carrier coordinate to inspect.

Next apply
\autoref{thm:critical-line-witness-root-comparison-ledger} and
\autoref{thm:critical-line-witness-root-strip-comparison-classifier}. The
comparison ledger $Q$ is transported only with $M,R,H,C,P,N$, and the
zero-strip side shares the same componentwise $\hsame$ and displayed $\Cont$
routes.

It remains to exclude alternate ledger sources. Use
\autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. The
refusal ledger has no slot for analytic continuation, quotient data, host
equality, ambient completeness, or an $\mathsf{RH}$ proof, so the stable
comparison is precisely the displayed finite-budget ledger.
\end{proof}

\begin{theorem}[Critical-line witness root finite-budget RH refusal non-escape]
\label{thm:critical-line-witness-root-finite-budget-rh-refusal-nonescape}
Every $\mathsf{RH}$-facing consumer of the root finite-budget surface of an
accepted $\CriticalLineWitnessUp$ packet receives only the finite refusal
package over
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer may cite the zero-strip source, rational modulus ledger,
comparison row, $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local
$\NameCert$ row, but it cannot extract $\mathsf{RH}$, analytic continuation, a
standard bridge, a global zero classifier, quotient equality, host equality, or
ambient completeness.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:critical-line-witness-root-finite-budget-source-totality}. It
identifies the root finite-budget source as a finite packet over the displayed
source, modulus, comparison, and structural rows.

Then use
\autoref{thm:critical-line-witness-root-finite-budget-ledger-stability}. Any
presentation of the same finite source keeps the rational ledger on the same
$\hsame/\Cont/\Pkg/\NameCert$ route.

Finally apply
\autoref{thm:critical-line-witness-rh-nonescape-package} and
\autoref{thm:critical-line-witness-root-refusal-downstream-gate}. These
refusal rows make the RH-facing export a finite boundary only; analytic
continuation, standard bridges, global zero classification, quotient equality,
host equality, ambient completeness, and $\mathsf{RH}$ proof data are absent
from the packet.
\end{proof}
