\begin{definition}[CriticalLineWitness root source window]
\label{def:critical-line-witness-window-source}
For an accepted $\CriticalLineWitnessUp$ root read, the root source window is
the finite $\BHist$ packet
$$
W_{\mathrm{src}}=(Z,S,M,H,C,P,N).
$$
Here $Z$ is the zero-strip source row, $S$ is the critical-line strip row, $M$
is the finite modulus and readback row, $H$ records the componentwise $\hsame$
transports, $C$ records the displayed $\Cont$ routes, $P$ records $\Pkg$
provenance over $\BHist$, $\hsame$, $\Cont$, and $\NameCert$, and $N$ is the
local $\NameCert_{\CriticalLineWitnessUp}$ row. A read is accepted by the
window only when every consumer-facing coordinate factors through these seven
rows before it reaches the full packet of \autoref{def:critical-line-witness-carrier}.
\end{definition}

\begin{theorem}[CriticalLineWitness zero-strip source separation]
\label{thm:critical-line-witness-zero-strip-separation}
Every accepted root source window
$W_{\mathrm{src}}=(Z,S,M,H,C,P,N)$ separates zero-strip source reads from
$\mathsf{RH}$ predicates, non-trivial-zero locators, global zero classifiers,
and completed $\GammaUp$ certificates. The only positive source reads exposed
by the window are the finite $\BHist$ rows $Z,S,M$, their componentwise
$\hsame$ transports $H$, their displayed $\Cont$ routes $C$, their $\Pkg$
provenance $P$, and the local $\NameCert_{\CriticalLineWitnessUp}$ row $N$.
\end{theorem}
\begin{proof}
Project the accepted read through
\autoref{def:critical-line-witness-window-source}. The projection exposes
only the seven displayed rows $Z,S,M,H,C,P,N$, so the zero-strip source side is
already a finite $\BHist$ packet before any downstream request is considered.

Next apply the source-route and zero-strip surfaces already present in
\autoref{thm:critical-line-witness-source-route-totality} and
\autoref{thm:critical-line-witness-zero-strip-source-totality}. These rows
force the supplied source, critical strip, modulus, transport, route,
provenance, and local naming coordinates to be read together.

Finally use the refusal and readback boundaries
\autoref{thm:critical-line-witness-rh-refusal-readback-totality} and
\autoref{thm:critical-line-witness-rh-boundary-refusal-totality}. They remove
the $\mathsf{RH}$ predicate, non-trivial-zero locator, global zero classifier,
and completed $\GammaUp$ certificate from the root window, leaving only the
finite source packet claimed above.
\end{proof}

\begin{theorem}[CriticalLineWitness continuation route coverage]
\label{thm:critical-line-witness-continuation-route-coverage}
Every downstream critical-strip consumer of an accepted
$\CriticalLineWitnessUp$ root source window must read the zero-strip source row
$Z$, the critical-line strip row $S$, the finite modulus row $M$, the
componentwise $\hsame$ transport row $H$, the displayed $\Cont$ route $C$, the
$\Pkg$ provenance row $P$, and the local $\NameCert_{\CriticalLineWitnessUp}$
row $N$ before consuming the witness. No downstream critical-strip read has a
coordinate outside
$$
Z,S,M,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Start with coordinate exhaustion for the root source window. By
\autoref{def:critical-line-witness-window-source}, an accepted window contains
only $Z,S,M,H,C,P,N$, and any consumer-facing coordinate must factor through
one of those rows before reaching the full carrier.

Read the critical-strip side through
\autoref{thm:critical-line-witness-modulus-strip-source-totality}. It places
the source row, fixed strip row, rational modulus data, transport, route,
provenance, and naming row before an $\mathsf{RH}$-refusal consumer can
inspect the witness.

It remains to account for route locality. The $\Cont$ component is displayed
as $C$ and is tied to the same packet by the source-route totality and local
NameCert obligations. Hence a downstream consumer cannot bypass $H,C,P,N$ or
replace them by an ambient continuation theorem; every route into the witness
is covered by the finite window rows.
\end{proof}
