\begin{theorem}[CriticalLineWitness source-route totality]
\label{thm:critical-line-witness-source-route-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Before any critical-line consumer reads $W$, the packet exposes its supplied
$\BHist$ source row $Z$, fixed zero-strip row $S$, rational modulus row $M$,
zeta-continuation witness row, comparison ledger rows $R,Q$, componentwise
$\hsame$ transport row $H$, displayed $\Cont$ route $C$, $\Pkg$ provenance row
$P$, and local $\NameCert_{\CriticalLineWitnessUp}$ row $N$. The consumer
therefore enters the packet only through the finite source route
$$
Z,S,M,R,Q,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Start with the root source triad of
\autoref{thm:critical-line-witness-root-source-triad}. It exposes the supplied
zero row, fixed critical-strip row, and source-facing comparison row as finite
$\BHist$ data before a critical-line consumer can inspect the packet.

Next apply the root comparison ledger
\autoref{thm:critical-line-witness-root-comparison-ledger} and the root modulus
readback theorem \autoref{thm:critical-line-witness-root-modulus-readback}.
These rows attach the rational modulus, real-part, and rational-comparison
coordinates to $M,R,Q,H,C,P,N$ rather than to a host analytic object.

Finally use the NameCert obligations of
\autoref{thm:critical-line-witness-namecert-obligations}. Carrier admission,
transport, displayed continuation, provenance, and local naming are all read
on the same accepted tuple, so no critical-line consumer can read $W$ before
the displayed source route has been exposed.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_source\_route\_totality}

\begin{theorem}[CriticalLineWitness zeta-boundary non-escape]
\label{thm:critical-line-witness-zeta-boundary-nonescape}
For an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, every zeta-facing read of $W$ remains inside the finite
$\ZetaContinuationWitnessUp$ ledger carried by the supplied source row and the
displayed route $Z,S,M,R,Q,H,C,P,N$. Such a read cannot import an
$\mathsf{RH}$ predicate, a global zero classifier, a completed $\GammaUp$
certificate, or a selected non-trivial-zero locator.
\end{theorem}
\begin{proof}
Read the supplied source through
\autoref{thm:critical-line-witness-source-route-totality}. The
critical-line witness has already exposed the zeta-continuation witness row and
the structural rows $H,C,P,N$ before any zeta-facing consumer can use it.

Now apply the ZetaContinuationWitness source obligation and analytic readback
obligation,
\autoref{thm:zeta-continuation-witness-source-obligation} and
\autoref{thm:zeta-continuation-witness-analytic-readback-obligation}. They keep
zeta-facing reads inside the displayed continuation ledger and its pole,
functional-equation, Gamma-boundary, transport, continuation, provenance, and
local naming rows.

Close with the ZetaContinuationWitness zero ledger non-escape theorem
\autoref{thm:zeta-continuation-witness-zero-ledger-nonescape}. It refuses
$\mathsf{RH}$ predicates, non-trivial-zero locators, global zero classifiers,
and completed Gamma certificates, so the CriticalLineWitness read cannot gain
those objects by passing through the supplied zeta ledger.
\end{proof}

\begin{theorem}[CriticalLineWitness NameCert obligation triad]
\label{thm:critical-line-witness-namecert-obligation-triad}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, the
source-route totality of
\autoref{thm:critical-line-witness-source-route-totality}, the zeta-boundary
non-escape of \autoref{thm:critical-line-witness-zeta-boundary-nonescape}, and
the modulus readback of
\autoref{thm:critical-line-witness-root-modulus-readback} form the local root
$\NameCert_{\CriticalLineWitnessUp}$ obligation triad. Together they expose the
finite $\BHist$ source, rational modulus, zeta-continuation, zero-strip,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows while refusing every off-packet
analytic, zero-classification, and host-equality exit.
\end{theorem}
\begin{proof}
The source-route totality theorem supplies the carrier side of the triad. It
projects the accepted packet to the displayed finite rows
$Z,S,M,R,Q,H,C,P,N$ before a critical-line consumer can read the witness.

The zeta-boundary non-escape theorem supplies the analytic boundary side. It
keeps zeta-facing reads inside the finite $\ZetaContinuationWitnessUp$ ledger
and refuses RH, zero-classifier, Gamma-completion, and non-trivial-zero
selection exits.

The modulus readback theorem supplies the numeric side. It routes rational
modulus, real-part, and rational comparison reads through $M,R,Q,H,C,P,N$ and
not through a host numeric oracle or quotient representative.

Combining these three coordinates gives exactly the local root
$\NameCert_{\CriticalLineWitnessUp}$ surface: source totality, boundary
non-escape, and modulus readback are all obligations over the same displayed
packet and no further root obligation row is introduced.
\end{proof}
