\begin{theorem}[Critical-line witness root downstream package]
\label{thm:critical-line-witness-root-downstream-package}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every downstream root-facing read factors through the supplied zero row $Z$, critical-strip row $S$, modulus row $M$, real-part row $R$, rational comparison ledger $Q$, displayed $\hsame$ transport row $H$, displayed $\Cont$ route row $C$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $N$.

The package excludes $\mathsf{RH}$ proof data, global zero classifiers, analytic-continuation certificates, quotient representatives, host equality, and ambient completeness.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:critical-line-witness-carrier}. The downstream source has exactly the rows $Z,S,M,R,Q,H,C,P,N$ available, with $Z$ and $S$ supplied before the modulus and comparison ledger are read.

Use the root non-escape package of \autoref{thm:critical-line-witness-root-nonescape-package}. It assembles the zero-strip route, modulus ledger route, and local BEDC rows as the root-facing export.

Finally apply the RH-refusal ledger completeness theorem \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. It removes $\mathsf{RH}$ proof data, global zero classification, analytic continuation, quotient representatives, host equality, and ambient completeness from every downstream read of the package.
\end{proof}

\begin{theorem}[Critical-line witness root carrier projection]
\label{thm:critical-line-witness-root-carrier-projection}
For every accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, the downstream root carrier projection is exactly the finite projection to the rows $Z,S,M,R,Q,H,C,P,N$. The projection preserves the supplied zero row, critical-strip row, modulus row, rational comparison ledger, transport row, continuation route, provenance row, and local naming row, and it forgets no row that a downstream root consumer is allowed to inspect.
\end{theorem}
\begin{proof}
Begin with the carrier-admission row of \autoref{thm:critical-line-witness-obligation-carrier-admission-row}. It identifies the accepted object with the displayed finite $\BHist$ tuple and leaves no hidden host coordinate behind the packet.

Apply the root source triad theorem \autoref{thm:critical-line-witness-root-source-triad}. The supplied zero, strip, and rational comparison rows remain exposed as the source side of the downstream boundary.

The modulus comparison route totality theorem \autoref{thm:critical-line-witness-modulus-comparison-route-totality} supplies the remaining modulus, real-part, transport, continuation, package, and naming coordinates. Combining these two projections gives exactly $Z,S,M,R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness root refusal consumer exactness]
\label{thm:critical-line-witness-root-refusal-consumer-exactness}
Every downstream consumer of the root-facing $\CriticalLineWitnessUp$ package is exact for the refusal boundary: it may cite the supplied zero row, critical-strip row, modulus row, real-part row, rational comparison ledger, displayed $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row, and it may cite nothing else as root evidence.

In particular, the consumer cannot extract an $\mathsf{RH}$ proof, a global zero classifier, an analytic-continuation certificate, a quotient representative, host equality, or ambient completeness from the accepted packet.
\end{theorem}
\begin{proof}
First read the downstream package of \autoref{thm:critical-line-witness-root-downstream-package}. It supplies the complete row list that a downstream consumer may cite.

Next project through \autoref{thm:critical-line-witness-root-carrier-projection}. This shows that the consumer's root evidence is not a larger analytic object; it is the same finite carrier projection $Z,S,M,R,Q,H,C,P,N$.

Finally apply the root refusal route of \autoref{thm:critical-line-witness-root-refusal-route}. The refusal route excludes $\mathsf{RH}$ proof data, zero search, global zero classification, analytic continuation, quotient representatives, host equality, and ambient completeness, so the consumer boundary is exact for the displayed packet.
\end{proof}

\begin{theorem}[Critical-line witness root dependency scope]
\label{thm:critical-line-witness-root-dependency-scope}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
The root downstream dependency scope of $W$ is exactly the finite route through
the supplied $\ZetaZerosUp$ row $Z$, supplied $\CritStripUp$ row $S$,
$\NatUp$ depth requests for the modulus row $M$, the $\RealUp$ real-part row
$R$, the $\RatUp$ comparison ledger $Q$, and the displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows $H,C,P,N$.

The scope contains no $\mathsf{RH}$ proof data, global zero classifier, analytic
continuation certificate, quotient representative, host equality, detached zero
oracle, or ambient completeness row.
\end{theorem}
\begin{proof}
Begin with the downstream package of
\autoref{thm:critical-line-witness-root-downstream-package}. It gives every
root-facing consumer the finite row list $Z,S,M,R,Q,H,C,P,N$ and excludes the
analytic and quotient data outside that list.

Next use the carrier projection of
\autoref{thm:critical-line-witness-root-carrier-projection}. The projection
identifies those rows as the complete finite carrier surface available to the
consumer, with no extra root evidence hidden behind the packet.

Finally combine the root modulus ledger scope of
\autoref{thm:critical-line-witness-root-modulus-ledger-scope} with the root
zero-strip exclusion of
\autoref{thm:critical-line-witness-root-zero-strip-exclusion}. The first binds
$M,R,Q,H,C,P,N$ to the modulus and rational-comparison route, while the second
binds $Z,S$ to the supplied zero-strip source. Together they give exactly the
dependency scope stated above.
\end{proof}

\begin{theorem}[Critical-line witness downstream refusal factorization]
\label{thm:critical-line-witness-downstream-refusal-factorization}
Every downstream refusal read of an accepted $\CriticalLineWitnessUp$ packet
factors through the dependency scope of
\autoref{thm:critical-line-witness-root-dependency-scope}. A refusal consumer
may cite the supplied zero row, strip row, modulus row, real-part row, rational
comparison ledger, transport, continuation, provenance, and local naming row,
and it may cite no additional RH-facing proof surface.
\end{theorem}
\begin{proof}
First read the exact consumer boundary of
\autoref{thm:critical-line-witness-root-refusal-consumer-exactness}. It states
that a downstream consumer may cite only $Z,S,M,R,Q,H,C,P,N$ as root evidence.

Now apply the dependency scope theorem just established. The allowed rows are
not an unstructured list: $Z$ and $S$ are the supplied
$\ZetaZerosUp$--$\CritStripUp$ source, $M$ is read at $\NatUp$ depths, $R$ is
the $\RealUp$ row, $Q$ is the $\RatUp$ comparison ledger, and $H,C,P,N$ are the
BEDC transport, route, provenance, and naming rows.

Finally use the RH-boundary refusal of
\autoref{thm:critical-line-witness-root-rh-boundary-refusal}. It removes
$\mathsf{RH}$ proof data, global zero classifiers, zero search, analytic
continuation, quotient representatives, host equality, and ambient completeness
from the downstream route, so every refusal read factors through the named
scope.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip-modulus package exhaustion]
\label{thm:critical-line-witness-zero-strip-modulus-package-exhaustion}
For an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, the supplied zero row, supplied critical-strip row,
modulus row, real-part row, and rational comparison ledger exhaust the root
package together with $H,C,P,N$. There is no remaining coordinate from which a
consumer can read another zero source, another strip certificate, another
modulus, another rational comparison row, an RH proof, analytic continuation,
host equality, quotient representatives, or ambient completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:critical-line-witness-root-dependency-scope}. It
identifies the full dependency route as
$Z,S,M,R,Q,H,C,P,N$ over $\ZetaZerosUp$, $\CritStripUp$, $\NatUp$, $\RealUp$,
$\RatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Use the root modulus ledger scope to exhaust the modulus and rational
comparison side. Every modulus or comparison read is already forced through
$M,R,Q,H,C,P,N$.

Use the root zero-strip exclusion to exhaust the zero and strip side. The
supplied rows $Z$ and $S$ stay attached to the same displayed history and cannot
be replaced by a detached oracle or analytic certificate.

Finally apply the RH-boundary refusal. Since the refusal boundary exports only
the finite package and none of the excluded analytic or host-level data, the
zero, strip, modulus, and rational comparison rows listed above exhaust the
root package.
\end{proof}
