\begin{theorem}[CriticalLineWitness supplied source carrier triad exhaustion]
\label{thm:critical-line-witness-supplied-source-carrier-triad-exhaustion}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The supplied $Z,S,Q$ source triad is exhausted by the displayed carrier rows $Z,S,M,R,Q,H,C,P,N$: $Z$ supplies the zero-facing source, $S$ supplies the critical-line strip, $Q$ supplies the source-facing comparison ledger, and the remaining rows $M,R,H,C,P,N$ only route, transport, replay, package, and name that same finite carrier.

No root read of the supplied source triad exports an $\mathsf{RH}$ proof object, a global zero search, analytic continuation, quotient representatives, host equality, or ambient completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:critical-line-witness-root-source-triad}. It identifies $Z,S,Q$ as the source triad exposed by the accepted root packet, and it reads that triad through the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ surface.

Project the carrier coordinates of $W$. The only available rows are $Z,S,M,R,Q,H,C,P,N$, so the triad cannot acquire a second zero source, detached strip witness, hidden comparison classifier, or ambient analytic row.

Finally route the unused carrier rows as support rows. The modulus, real-part, transport, continuation, provenance, and naming coordinates preserve the same finite packet rather than adding a proof of $\mathsf{RH}$ or any external completion datum.
\end{proof}

\begin{theorem}[CriticalLineWitness modulus comparison NameCert route]
\label{thm:critical-line-witness-modulus-comparison-namecert-route}
For every accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, every modulus comparison read factors through $M,R,Q,H,C,P,N$ and the local $\NameCert_{\CriticalLineWitnessUp}$ row. The route exposes the modulus row $M$, real-part row $R$, rational comparison row $Q$, componentwise transport row $H$, displayed continuation row $C$, package provenance row $P$, and local naming row $N$ before any comparison-facing consumer can read the packet.

The route does not supply a host analytic estimate, quotient representative, global zero classifier, analytic-continuation certificate, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Apply \autoref{thm:critical-line-witness-root-comparison-ledger}. It places comparison reads on the finite ledger containing $M,R,Q,H,C,P,N$ and refuses replacement by global zero, quotient, analytic, or completeness data.

Next apply \autoref{thm:critical-line-witness-modulus-comparison-route-totality}. The modulus row and rational comparison row are consumed under the same transport, continuation, provenance, and local naming rows, so the $\NameCert_{\CriticalLineWitnessUp}$ coordinate belongs to the comparison route itself.

The carrier projection supplies no further comparison coordinate. Thus every accepted modulus comparison read factors through exactly the displayed NameCert route.
\end{proof}

\begin{theorem}[CriticalLineWitness RH refusal public nonescape]
\label{thm:critical-line-witness-rh-refusal-public-nonescape}
Every public $\mathsf{RH}$-facing read of an accepted $\CriticalLineWitnessUp$ packet exposes only the displayed finite refusal route through $Z,S,M,R,Q,H,C,P,N$. It cannot export an $\mathsf{RH}$ proof, zero search, analytic continuation, quotient representative, host equality, ambient completeness, or any detached classifier outside the packet.

The public route is therefore a finite refusal surface over the supplied source rows, modulus comparison rows, transport rows, continuation rows, provenance row, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Use \autoref{thm:critical-line-witness-root-refusal-route} to locate every public refusal read on the root packet. The refusal is carried by the displayed finite rows rather than by an external analytic certificate or host-level equality.

Then apply \autoref{thm:critical-line-witness-rh-refusal-nonescape}. This excludes $\mathsf{RH}$ proof data, zero search, analytic continuation, quotient representatives, host equality, and ambient completeness from the accepted packet surface.

Combining the two routes leaves only $Z,S,M,R,Q,H,C,P,N$. The public read can refuse off-route demands, but it has no coordinate from which to export the forbidden data.
\end{proof}
