\begin{theorem}[Critical-line witness carrier route exactness]
\label{thm:critical-line-witness-carrier-route-exactness}
Let $W$ be an accepted $\CriticalLineWitnessUp$ packet. The carrier route exposed by $W$ is exactly the finite tuple
$$
Z,S,M,R,Q,H,C,P,N.
$$
Here $Z$ is the supplied $\ZetaZerosUp$ zero row, $S$ is the $\CritStripUp$ strip row, $M$ is the depth row, $R$ is the real-part row, $Q$ is the rational comparison row, and $H,C,P,N$ are the displayed transport, continuation, provenance, and local $\NameCert_{\CriticalLineWitnessUp}$ rows. No accepted packet exposes a tenth carrier coordinate.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:critical-line-witness-carrier}. Its public coordinates are the zero, strip, depth, real-part, rational comparison, transport, continuation, provenance, and local naming rows.

Use the fixed-strip tuple of \autoref{def:critical-line-witness-fixed-strip-source-tuple} and the row exhaustion theorem \autoref{thm:critical-line-witness-fixed-strip-row-exhaustion}. They identify the visible fixed-strip source route with the nine displayed rows and exclude any additional analytic, quotient, host-equality, or completeness coordinate.

Finally apply \autoref{thm:critical-line-witness-root-route-exposure}. Every downstream zeta or $\mathsf{RH}$ route first exposes the same source, modulus, refusal, transport, continuation, package, and naming surface. Hence the accepted packet exposes exactly $Z,S,M,R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness modulus route totality]
\label{thm:critical-line-witness-modulus-route-totality}
For every accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, every depth or modulus request is total as a finite route: it factors through
$$
M,R,Q,H,C,P,N
$$
or it lands in the visible refusal ledger of $W$. The request cannot be completed by a hidden modulus source, analytic-continuation primitive, host equality, quotient representative, ambient completeness row, or proof of $\mathsf{RH}$.
\end{theorem}
\begin{proof}
Start with the carrier route exactness theorem \autoref{thm:critical-line-witness-carrier-route-exactness}. It leaves only the displayed packet rows available to an accepted depth or modulus read.

Apply the modulus readback row \autoref{thm:critical-line-witness-modulus-readback-row} and the source-modulus refusal totality theorem \autoref{thm:critical-line-witness-source-modulus-refusal-totality}. Accepted requests pass through $M,R,Q$ together with the transport, continuation, package, and naming rows; absent or mismatched requests are sent to the visible refusal side.

Use the zero-strip modulus refusal theorem \autoref{thm:critical-line-witness-zero-strip-modulus-refusal}. It blocks reinterpretation of a failed modulus read as an $\mathsf{RH}$ coordinate, analytic-continuation coordinate, host zero classifier, quotient representative, or ambient completeness witness. Thus the finite route is total by acceptance or refusal.
\end{proof}

\begin{theorem}[Critical-line witness downstream RH boundary nonescape]
\label{thm:critical-line-witness-downstream-rh-boundary-nonescape}
Every downstream $\mathsf{RH}$-facing consumer of an accepted $\CriticalLineWitnessUp$ packet receives only the finite witness/refusal package
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer receives no proof of $\mathsf{RH}$, no zero search, no analytic-continuation primitive, no host equality, no quotient representative, and no ambient completeness datum.
\end{theorem}
\begin{proof}
First apply \autoref{thm:critical-line-witness-carrier-route-exactness}. It fixes the carrier route available to downstream consumers at the nine displayed rows.

Next apply \autoref{thm:critical-line-witness-modulus-route-totality}. Depth and modulus requests either pass through $M,R,Q,H,C,P,N$ or land in the visible refusal ledger, so the downstream consumer has no alternate modulus or comparison source.

Finally use the RH consumer boundary theorem \autoref{thm:critical-line-witness-rh-consumer-boundary} and the downstream refusal package \autoref{thm:critical-line-witness-downstream-refusal-package}. These rows identify the consumer-facing object as a finite witness/refusal boundary and exclude proof, search, analytic-continuation, host-equality, quotient, and completeness exports.
\end{proof}
