\begin{theorem}[CriticalLineWitness root source-window route lock]
\label{thm:critical-line-witness-root-source-window-route-lock}
Let $W$ be an accepted $\CriticalLineWitnessUp$ root packet. Its $\BHist$ source rows, zero-strip source rows, modulus-window comparison rows, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row form one finite root source-window route. Every RH-facing consumer read of $W$ factors through that route and cannot attach a second analytic source, second modulus window, hidden zero oracle, ambient zeta equality, or host-level RH decision row.
\end{theorem}
\begin{proof}
Start from the root source exposure package and the finite route scope for $\CriticalLineWitnessUp$. These rows expose the root source, strip source, modulus comparison, transport, continuation, provenance, and local name as finite $\BHist$ coordinates.

The route lock is then componentwise. The $\hsame$ rows transport the source and modulus coordinates already displayed by the carrier, while the $\Cont$ rows replay only those transported coordinates for downstream consumers.

Since the $\Pkg$ and $\NameCert$ rows record the same finite route, a consumer cannot project an additional analytic source, hidden zero oracle, ambient zeta equality, or host RH decision from the packet. Those coordinates are not carrier rows and are therefore outside the root read.
\end{proof}

\begin{theorem}[CriticalLineWitness root modulus comparison exhaustion]
\label{thm:critical-line-witness-root-modulus-comparison-exhaustion}
Every modulus-comparison read admitted by a $\CriticalLineWitnessUp$ root packet is exhausted by the displayed $\BHist$ source row, zero-strip row, finite modulus-window row, $\hsame$ transport row, $\Cont$ replay row, $\Pkg$ provenance row, and local $\NameCert$ row. The comparison may certify the availability and transport of the displayed modulus data, but it does not assert a zero count, a zero-free strip, or the Riemann hypothesis.
\end{theorem}
\begin{proof}
Use the root source-modulus interface to locate the comparison inside the source and window rows of the accepted packet. The comparison is a finite ledger read over those rows, not a theorem about the zero set itself.

Apply the root modulus readback and source-modulus closure rows. They show that transporting a displayed comparison by $\hsame$ and replaying it by $\Cont$ keeps the read inside the same finite $\BHist$ route and the same $\Pkg$ provenance.

The final boundary is the local $\NameCert$ exactness row. It permits the consumer to read the supplied modulus comparison and its provenance, while zero counts, zero-free-strip conclusions, and RH conclusions remain outside the packet.
\end{proof}

\begin{theorem}[CriticalLineWitness root RH consumer refusal totality]
\label{thm:critical-line-witness-root-rh-consumer-refusal-totality}
Every RH-facing consumer request to a $\CriticalLineWitnessUp$ root packet is total as a finite readback and total as a refusal boundary: accepted reads return only the displayed $\BHist$ source, modulus comparison, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, while requests for a zero theorem, a zero-free critical strip, a hidden analytic continuation equality, a completed RH proof row, or a host RH truth value are refused.
\end{theorem}
\begin{proof}
First read the accepted side through the root source-window route lock of \autoref{thm:critical-line-witness-root-source-window-route-lock}. It gives every RH-facing consumer the finite source, modulus, transport, continuation, provenance, and naming rows already present in the packet.

Next apply the modulus comparison exhaustion of \autoref{thm:critical-line-witness-root-modulus-comparison-exhaustion}. The comparison row is available as a displayed finite obligation row, but it is not a zero-counting row and not an RH row.

The refusal side follows from the same inventory. A zero theorem, zero-free critical strip, hidden analytic continuation equality, completed RH proof row, or host RH truth value would require a coordinate absent from $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ for this packet, so the request is refused rather than exported.
\end{proof}
