\begin{theorem}[Critical-line witness source-modulus exclusion]
\label{thm:criticallinewitness-source-modulus-exclusion}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every source-modulus consumer of $W$ must read the supplied $\ZetaZerosUp$ row $Z$, the $\CritStripUp$ row $S$, the $\NatUp$ modulus row $M$, the $\RealUp$ real-part row $R$, the $\RatUp$ comparison ledger $Q$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows before it can inspect any downstream boundary. The route exports no global zero classification, analytic-continuation theorem, host equality, quotient representative, $\mathsf{RH}$ proof content, or hidden ambient completeness datum.
\end{theorem}
\begin{proof}
Begin with the source normalization interface. \autoref{thm:critical-line-witness-source-normalization-interface} exposes the supplied zero row, critical-strip row, Nat depth row, rational comparison ledger, and real-part row as the finite packet $Z,S,M,R,Q,H,C,P,N$.

Next apply the root source-modulus admission theorem. \autoref{thm:critical-line-witness-root-source-modulus-admission} places every source-modulus read after the displayed zero-strip source and comparison rows, under the same transport, continuation, package, and local naming surface.

Finally use the RH refusal interface. \autoref{thm:critical-line-witness-rh-refusal-interface} classifies requests for global zero classification, analytic continuation, host equality, quotient representatives, proof content, and ambient completeness as refusal-side requests rather than source-modulus data. The admitted consumer is therefore confined to $Z,S,M,R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip route totality]
\label{thm:criticallinewitness-zero-strip-route-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every zero-strip route used by a root, zeta-facing, or $\mathsf{RH}$-boundary consumer is total through the displayed source-modulus packet
$$
Z,S,M,R,Q,H,C,P,N.
$$
The route reads the supplied zero row, critical-strip row, modulus row, real-part row, rational comparison ledger, componentwise transport, displayed continuation, provenance, and local naming, and it cannot read a global zero classifier, analytic-continuation certificate, host equality, quotient representative, or $\mathsf{RH}$ proof.
\end{theorem}
\begin{proof}
First use source-modulus exclusion. It confines the consumer to the packet $Z,S,M,R,Q,H,C,P,N$ before any zero-strip or boundary read is available.

Now apply the zero-strip budget factorization theorem \autoref{thm:critical-line-witness-zero-strip-budget-factorization}. That theorem identifies zero-strip budget requests with the supplied $Z,S$ rows and the shared modulus ledger $M,R,Q,H,C,P,N$.

Finally use the zeta-consumer non-escape theorem \autoref{thm:critical-line-witness-zeta-consumer-nonescape}. Zeta-facing and $\mathsf{RH}$-facing consumers remain on the same finite readback surface, so totality of the zero-strip route carries no analytic-continuation, host-equality, quotient, global-classifier, or proof-content coordinate.
\end{proof}

\begin{theorem}[Critical-line witness RH-boundary nonescape]
\label{thm:criticallinewitness-rh-boundary-nonescape}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every $\mathsf{RH}$-boundary consumer whose read is served by the source-modulus and zero-strip rows of $W$ is exhausted by $Z,S,M,R,Q,H,C,P,N$. It may read the displayed source row, strip row, modulus row, real-part row, rational comparison ledger, $\BHist$ history, $\hsame$ transports, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, but it cannot read global zero classification, analytic continuation, host equality, quotient representatives, or $\mathsf{RH}$ proof content.
\end{theorem}
\begin{proof}
Start with zero-strip route totality. The boundary consumer has already been routed through $Z,S,M,R,Q,H,C,P,N$ and has no second zero-strip or host-real channel.

Next apply \autoref{thm:critical-line-witness-rh-boundary-refusal-exhaustion}. The RH-boundary side is exhausted by the locked source side $Z,S$, the total modulus ledger $M,R,Q$, and the structural rows $H,C,P,N$.

Finally combine this with \autoref{thm:critical-line-witness-downstream-rh-boundary-nonescape}. Downstream consumers receive a refusal packet rather than an analytic claim, so global zero classification, analytic continuation, host equality, quotient representatives, and proof content have no carrier row from which to escape.
\end{proof}
