\begin{theorem}[Critical-line witness downstream RH boundary refinement]
\label{thm:critical-line-witness-downstream-rh-boundary-refinement}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every downstream RH-facing read of $W$ is exhausted by the displayed finite rows
$$
Z,S,M,R,Q,H,C,P,N.
$$
The supplied zero-strip route, the modulus ledger entry, the RH non-escape package, the root source triad, and the root comparison ledger together force each read through the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No downstream consumer receives analytic continuation, quotient representatives, host equality, ambient completeness, a global zero classifier, or an $\mathsf{RH}$ proof from this boundary.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_downstream\_rh\_boundary\_refinement}
\begin{proof}
Begin with the supplied zero-strip route of \autoref{thm:critical-line-witness-supplied-zero-strip-route}. It identifies the zero and strip reads with the finite route $Z,S,H,C,P,N$.

Next use the modulus ledger entry of \autoref{thm:critical-line-witness-modulus-ledger-entry}. It places every modulus and rational-comparison request on $M,R,Q,H,C,P,N$.

The RH non-escape package of \autoref{thm:critical-line-witness-rh-nonescape-package} then removes analytic proof data, zero search, host equality, quotient representatives, analytic continuation, and ambient completeness from the downstream interface. The root source triad and root comparison ledger of \autoref{thm:critical-line-witness-root-source-triad} and \autoref{thm:critical-line-witness-root-comparison-ledger} identify the remaining source and comparison reads with the same displayed packet rows, so the boundary is exactly the finite read surface stated above.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip modulus route]
\label{thm:critical-line-witness-zero-strip-modulus-route}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The zero-strip route $Z,S,H,C,P,N$ and the modulus route $M,R,Q,H,C,P,N$ form one downstream RH-facing route over the same componentwise $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. A consumer that reads the supplied zero or critical-strip row and then asks for the modulus or rational comparison must stay inside $Z,S,M,R,Q,H,C,P,N$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:critical-line-witness-supplied-zero-strip-route} to obtain the supplied route for $Z$ and $S$. This route is carried by $H,C,P,N$ and excludes replacement by zero search, host equality, quotient representatives, analytic continuation, or completeness.

Apply \autoref{thm:critical-line-witness-modulus-ledger-entry} to obtain the modulus-facing route through $M,R,Q,H,C,P,N$. The shared rows $H,C,P,N$ keep the zero-strip and modulus reads on the same visible packet.

Finally combine \autoref{thm:critical-line-witness-root-source-triad}, \autoref{thm:critical-line-witness-root-comparison-ledger}, and \autoref{thm:critical-line-witness-rh-nonescape-package}. These results make the source triad and comparison ledger the only admissible downstream reads and refuse any analytic or host-level replacement.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_zero\_strip\_modulus\_route}

\begin{theorem}[Critical-line witness root source consumer totality]
\label{thm:critical-line-witness-root-source-consumer-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every root source consumer for a downstream RH-facing chapter is total on the displayed finite packet: it either reads the supplied zero-strip route, the modulus ledger entry, the root source triad, or the root comparison ledger, and each case factors through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $W$. There is no fifth consumer route requiring analytic continuation, quotient representatives, host equality, ambient completeness, a global zero classifier, or an $\mathsf{RH}$ proof.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_source\_consumer\_totality}
\begin{proof}
The supplied zero-strip route of \autoref{thm:critical-line-witness-supplied-zero-strip-route} covers zero and strip source reads. The modulus ledger entry of \autoref{thm:critical-line-witness-modulus-ledger-entry} covers depth, real-part, and rational-comparison reads.

The root source triad of \autoref{thm:critical-line-witness-root-source-triad} packages $Z,S,Q$ as the finite source rows available before a downstream boundary reads the packet. The root comparison ledger of \autoref{thm:critical-line-witness-root-comparison-ledger} packages the comparison side through $Q$ together with $M,R,H,C,P,N$.

Use the downstream RH boundary refinement of \autoref{thm:critical-line-witness-downstream-rh-boundary-refinement} and the RH non-escape package of \autoref{thm:critical-line-witness-rh-nonescape-package}. They exhaust the public reads by the displayed rows and remove the analytic, quotient, host-equality, completeness, global-zero, and RH-proof alternatives, so the listed source consumers are total for downstream use.
\end{proof}
