\begin{theorem}[Critical-line witness root route exposure]
\label{thm:critical-line-witness-root-route-exposure}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every accepted route that can feed a downstream zeta or $\mathsf{RH}$ consumer first exposes the critical-strip source, the zero-strip source and modulus row, the refusal ledger, the $\BHist$ carrier, the $\hsame$ transport row, the $\Cont$ replay row, the $\Pkg$ provenance row, and the local $\NameCert_{\CriticalLineWitnessUp}$ row. The route has no accepted read before the displayed source/modulus/refusal surface is present.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_route\_exposure}
\begin{proof}
Project the accepted carrier of \autoref{def:critical-line-witness-carrier}. Its displayed rows are the source rows $Z,S$, the modulus and comparison rows $M,R,Q$, and the structural rows $H,C,P,N$.

Apply the root source triad \autoref{thm:critical-line-witness-root-source-triad} and the zero-strip source totality row \autoref{thm:critical-line-witness-zero-strip-source-totality}. These rows expose the critical-strip and zero-strip source side as finite $\BHist$ data before any downstream read occurs.

Next use \autoref{thm:critical-line-witness-root-source-modulus-admission} and \autoref{thm:critical-line-witness-source-modulus-refusal-totality}. They attach the zero-strip modulus and refusal ledger to the same displayed package, carried through $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row.

Finally apply \autoref{thm:critical-line-witness-route-readback-exhaustion}. Every downstream zeta or $\mathsf{RH}$ readback is exhausted by this displayed package, so no accepted route can bypass the exposed source/modulus/refusal surface.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip modulus refusal]
\label{thm:critical-line-witness-zero-strip-modulus-refusal}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. If a zero-strip modulus read is absent from the displayed route or mismatches the displayed modulus row $M$, the read is routed to the visible refusal ledger of $W$. It is not reinterpreted as a hidden $\mathsf{RH}$ coordinate, an analytic-continuation coordinate, a host zero classifier, a quotient representative, or an ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:critical-line-witness-root-route-exposure}. Any accepted route has already exposed the zero-strip source, the modulus row, the refusal ledger, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Use the zero-strip source totality theorem \autoref{thm:critical-line-witness-zero-strip-source-totality}. It keeps the zero-strip source read inside the displayed finite route, rather than opening an analytic or host-level coordinate.

Apply \autoref{thm:critical-line-witness-modulus-refusal-readback} and \autoref{thm:critical-line-witness-source-modulus-refusal-totality}. A modulus readback that is missing or mismatched has only the displayed refusal side available, because the carrier exports no second modulus or hidden analytic continuation coordinate.

Finally use the downstream refusal package \autoref{thm:critical-line-witness-downstream-refusal-package}. The excluded $\mathsf{RH}$ proof, analytic-continuation certificate, host zero classifier, quotient representative, and ambient completeness witness are refusal-side requests, so the failed modulus read lands in the visible ledger.
\end{proof}

\begin{theorem}[Critical-line witness downstream readback exhaustion]
\label{thm:critical-line-witness-downstream-readback-exhaustion}
Every downstream $\ZetaZerosUp$, $\CritStripUp$, zeta-boundary, or $\mathsf{RH}$ consumer of an accepted $\CriticalLineWitnessUp$ packet reads only the displayed source-modulus-refusal package
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer cannot draw source, modulus, refusal, transport, continuation, package, or local naming data from a hidden analytic-continuation route, a host equality, a global zero classifier, a quotient representative, a selected completion coordinate, or an ambient completeness coordinate.
\end{theorem}
\begin{proof}
First apply \autoref{thm:critical-line-witness-root-route-exposure}. It places the critical-strip source, zero-strip source, modulus, refusal ledger, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows on the route before any downstream consumer reads the packet.

Next use the root $\mathsf{RH}$ boundary row \autoref{thm:critical-line-witness-root-source-lock}. This keeps the downstream boundary attached to the finite source/modulus surface instead of replacing it by an $\mathsf{RH}$ truth value or host analytic datum.

Apply \autoref{thm:critical-line-witness-zero-strip-modulus-refusal}. Missing or mismatched modulus requests are sent to the visible refusal ledger, so they cannot produce an alternate source for downstream zeta or $\mathsf{RH}$ consumers.

Finally invoke \autoref{thm:critical-line-witness-route-readback-exhaustion} and \autoref{thm:critical-line-witness-source-modulus-refusal-totality}. These rows exhaust downstream readback at the displayed source-modulus-refusal package, leaving no hidden coordinate from which another consumer route can be read.
\end{proof}
