\begin{theorem}[Critical-line witness root refusal budget completion]
\label{thm:critical-line-witness-root-refusal-budget-completion}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every root-facing critical-line witness request factors through the finite rows
$$
Z,S,M,R,Q,H,C,P,N
$$
before any $\mathsf{RH}$-facing consumer can read it. The route exposes only the supplied zero row, critical-strip row, modulus row, real-part row, rational comparison ledger, componentwise transport, continuation replay, package provenance, and local $\NameCert$ row.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_refusal\_budget\_completion}
\begin{proof}
Begin with the root source triad of \autoref{thm:critical-line-witness-root-source-triad}. It exposes $Z,S,Q$ as finite $\BHist$ source data before a downstream boundary can read the witness.

Next apply the root comparison ledger of \autoref{thm:critical-line-witness-root-comparison-ledger}. It places every root-facing rational comparison through $Q$ together with the displayed modulus, real-part, transport, continuation, package, and naming rows.

The remaining downstream read is governed by the RH-refusal ledger completeness theorem, \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. That ledger keeps the consumer inside $Z,S,M,R,Q,H,C,P,N$ and refuses every stronger analytic or RH-facing export.

Thus the root-facing request is complete as a finite refusal budget before any $\mathsf{RH}$-facing consumer receives the packet.
\end{proof}

\begin{theorem}[Critical-line witness zeta-strip modulus totality]
\label{thm:critical-line-witness-zeta-strip-modulus-totality}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, the displayed route through $\ZetaZerosUp$, $\CritStripUp$, $\RealUp$, and $\RatUp$ is total for the zero-strip modulus packet. It reads the zeta-zero surface, critical-strip boundary, real-part modulus row, and rational comparison ledger, and it exports no analytic-continuation row, host equality row, quotient row, or ambient-completeness row.
\end{theorem}
\begin{proof}
Use the zeta dependency lattice of \autoref{thm:critical-line-witness-zeta-link}. It places every zero-strip or critical-line read behind the existing $\ZetaZerosUp$ and RH-boundary surfaces before the local modulus witness is public.

The root source triad \autoref{thm:critical-line-witness-root-source-triad} supplies the finite $Z,S,Q$ side of this route. The root comparison ledger \autoref{thm:critical-line-witness-root-comparison-ledger} then supplies the $M,R,Q$ comparison side through $\RealUp$ and $\RatUp$ rows rather than through a host analytic object.

Finally, the RH-refusal ledger completeness theorem \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness} excludes analytic continuation, host equality, quotient representatives, and ambient completeness. Hence the displayed zeta-strip-modulus route is total exactly over the finite packet rows.
\end{proof}

\begin{theorem}[Critical-line witness RH consumer refusal exactness]
\label{thm:critical-line-witness-rh-consumer-refusal-exactness}
Every $\mathsf{RH}$-facing consumer of an accepted $\CriticalLineWitnessUp$ packet receives exactly the refusal ledger and finite witness boundary over
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer does not receive an $\mathsf{RH}$ proof, a global zero classifier, an analytic-continuation certificate, a quotient representative, host equality, or an ambient-completeness principle.
\end{theorem}
\begin{proof}
First read the refusal ledger through \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. It states that downstream $\mathsf{RH}$-facing access is exhausted by the displayed rows and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ structure.

Next use the root source triad and root comparison ledger, \autoref{thm:critical-line-witness-root-source-triad} and \autoref{thm:critical-line-witness-root-comparison-ledger}. Together they identify the finite witness boundary that the consumer may cite: the supplied zero and strip rows, the modulus and real-part rows, the rational comparison ledger, and the structural rows.

The zeta dependency lattice of \autoref{thm:critical-line-witness-zeta-link} fixes the sibling source of the zero-strip read without adding an analytic proof surface. Therefore the consumer receives the refusal ledger exactly, not an $\mathsf{RH}$ proof or global zero classifier.
\end{proof}
