\begin{theorem}[CriticalLineWitness route classifier exhaustion]
\label{thm:critical-line-witness-route-classifier-exhaustion}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Every accepted classifier read of $W$ is exhausted by the finite zero-strip,
modulus, comparison, transport, continuation, provenance, and local
$\NameCert_{\CriticalLineWitnessUp}$ rows
$$
Z,S,M,R,Q,H,C,P,N .
$$
The read has no accepted coordinate for host equality, zero search,
analytic-continuation certificates, quotient representatives, ambient
completeness, a global zero classifier, or a proof of $\mathsf{RH}$.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessRouteClassifierExhaustion}
\begin{proof}
Start with classifier exactness,
\autoref{thm:critical-line-witness-classifier-exactness}. It identifies the
root classifier with the supplied zero row $Z$, the supplied critical-strip
row $S$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local
$\NameCert_{\CriticalLineWitnessUp}$ surface carried by $H,C,P,N$.

Next apply ledger route stability,
\autoref{thm:critical-line-witness-ledger-route-stability}. The modulus,
real-part, and rational-comparison rows $M,R,Q$ remain attached to the same
transport, replay, provenance, and naming route, so the classifier cannot
branch to an off-packet comparison or host representative.

Finally combine downstream consumer unblock,
\autoref{thm:critical-line-witness-downstream-consumer-unblock}, with
source-signature readback,
\autoref{thm:critical-line-witness-source-signature-readback}. These rows
make the finite packet the whole admitted source and consumer surface. Hence
every accepted classifier read is exhausted by
$Z,S,M,R,Q,H,C,P,N$ and every analytic, host, quotient, completeness, global
zero-classification, or $\mathsf{RH}$ demand is refused outside the route.
\end{proof}

\begin{theorem}[CriticalLineWitness fixed-strip zeta consumer separation]
\label{thm:critical-line-witness-fixed-strip-zeta-consumer-separation}
For an accepted fixed-strip $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, fixed-strip source reads and zeta-facing downstream
consumers remain separated by the displayed signature, gap, and ledger rows.
The fixed-strip side may read the supplied zero and strip rows $Z,S$, while
the zeta-facing consumer may read only the modulus, comparison, transport,
continuation, provenance, and naming rows $M,R,Q,H,C,P,N$ already displayed
by the same packet. No accepted consumer route imports an $\mathsf{RH}$ proof
or analytic-continuation certificate across that separation.
\end{theorem}
\begin{proof}
Read the source side through
\autoref{thm:critical-line-witness-source-signature-readback}. It places the
critical-strip source behind the displayed finite signature route and the
gap row, rather than behind a hidden analytic-continuation or host-zero
coordinate.

Apply gap-policy stability,
\autoref{thm:critical-line-witness-gap-policy-stability}. The displayed
$\hsame$ transport and $\Cont$ replay preserve refusal rows as refusal rows,
so moving along $H$ and $C$ cannot turn a missing analytic or $\mathsf{RH}$
coordinate into accepted source data.

Now use the fixed-strip zeta consumer boundary,
\autoref{thm:critical-line-witness-fixed-strip-zeta-consumer-boundary}, and
ledger route stability,
\autoref{thm:critical-line-witness-ledger-route-stability}. The zeta-facing
consumer receives the refusal budget and rational comparison ledger through
$M,R,Q,H,C,P,N$ on the same finite route.

Thus the fixed-strip source and downstream zeta consumer meet only at the
displayed signature, gap, and ledger rows. The route supplies no
$\mathsf{RH}$ proof, analytic-continuation certificate, host equality,
quotient representative, or ambient-completeness datum.
\end{proof}

\begin{theorem}[CriticalLineWitness finite NameCert consumer route]
\label{thm:critical-line-witness-finite-namecert-consumer-route}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Every accepted $\NameCert_{\CriticalLineWitnessUp}$ consumer route factors
through the displayed $\BHist$ carrier, $\hsame$ transport row, $\Cont$
replay row, $\Pkg$ provenance row, and local naming row of $W$. The route may
consume only the local source, signature, gap, modulus, comparison, and
refusal rows already named by $Z,S,M,R,Q,H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with NameCert route exhaustion,
\autoref{thm:critical-line-witness-namecert-route-exhaustion}. It already
forces accepted consumer routes through the packet-local $\BHist$, $\Cont$,
$\hsame$, $\Pkg$, and $\NameCert_{\CriticalLineWitnessUp}$ surface.

Attach the classifier and ledger rows. Classifier exactness
\autoref{thm:critical-line-witness-classifier-exactness} binds classifier
reads to $Z,S,H,C,P,N$, while ledger route stability
\autoref{thm:critical-line-witness-ledger-route-stability} binds comparison
reads to $M,R,Q,H,C,P,N$.

It remains to include the source and downstream interfaces. Source-signature
readback \autoref{thm:critical-line-witness-source-signature-readback} keeps
the source behind the displayed signature and gap rows, and downstream
consumer unblock \autoref{thm:critical-line-witness-downstream-consumer-unblock}
confines every consumer to the finite packet surface.

Therefore every accepted NameCert consumer route factors through the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local naming rows. A route
that asks for host equality, analytic continuation, quotient representatives,
ambient completeness, global zero classification, or an $\mathsf{RH}$ proof
is outside the accepted $\CriticalLineWitnessUp$ consumer route.
\end{proof}
