\begin{theorem}[CriticalLineWitness critical-strip source surface]
\label{thm:critical-line-witness-critical-strip-source}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Every accepted packet exposes the supplied critical-strip source row $S$,
together with its $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert_{\CriticalLineWitnessUp}$ routes, before any zero-line consumer,
modulus consumer, or $\mathsf{RH}$-facing consumer row can read the witness.
The exposed row is a packet source row, not a host critical-line theorem,
analytic continuation primitive, quotient equality, or standard-model
replacement.
\end{theorem}
\begin{proof}
Project $W$ through the carrier description of
\autoref{def:critical-line-witness-carrier}. The critical-strip coordinate
$S$ is one of the displayed finite $\BHist$ rows, and the only structural
routes attached to it are the local $H,C,P,N$ coordinates.

Apply the root-strip source totality theorem
\autoref{thm:critical-line-witness-root-strip-source-totality}. It places the
$\CritStripUp$ source row on the visible source route before any
critical-line-facing read is available.

Use the RH source lock
\autoref{thm:critical-line-witness-rh-source-lock} for downstream reads and
the zero-strip compatibility obligation
\autoref{thm:critical-line-witness-zero-strip-compatibility-obligation} for
zero-line reads. These rows force the supplied strip source to be visible
through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ before any
consumer reads the witness surface, and they leave no coordinate for a host
critical-line theorem, analytic primitive, quotient equality, or
standard-model replacement.
\end{proof}

\begin{theorem}[CriticalLineWitness zero-refusal locality]
\label{thm:critical-line-witness-zero-refusal-locality}
For an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, every zero-refusal row is local to the displayed
packet. The refusal is witnessed inside the finite $\BHist$ carrier, the
componentwise $\hsame$ transport row, the displayed $\Cont$ replay row, the
$\Pkg$ provenance row, and the local $\NameCert_{\CriticalLineWitnessUp}$
row; it is not a claim about an analytic zero primitive, global zero
classifier, host quotient equality, analytic-continuation theorem, or
$\mathsf{RH}$ truth value.
\end{theorem}
\begin{proof}
Start with the zero-strip refusal theorem
\autoref{thm:critical-line-witness-zero-strip-refusal}. It reads refusal as a
row of the accepted $\BHist$ packet and requires zero-strip consumers to pass
through the displayed source, budget, modulus, readback, and refusal rows.

Next apply the local transport obligation
\autoref{thm:critical-line-witness-hsame-cont-ledger-obligation}. The
componentwise $\hsame$ row, displayed $\Cont$ replay row, $\Pkg$ provenance,
and local $\NameCert$ replay are bound to the same zero-strip-modulus ledger.

Finally use the downstream refusal ledger
\autoref{thm:critical-line-witness-downstream-refusal-ledger}. It excludes
an analytic zero primitive, global zero classifier, quotient representative,
analytic-continuation certificate, ambient completeness witness, and
$\mathsf{RH}$ proof from downstream reads. The zero-refusal row is therefore
local to $W$ and does not export an analytic or host-level replacement.
\end{proof}

\begin{theorem}[CriticalLineWitness modulus budget totality]
\label{thm:critical-line-witness-modulus-budget-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
The modulus budget rows $M,R,Q,H,C,P,N$, read together with the supplied
source rows $Z,S$, exhaust every consumer read before any critical-line
witness is exported. A consumer can receive only the finite packet route
through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert_{\CriticalLineWitnessUp}$; it cannot bypass that budget by
requesting $\mathsf{RH}$ truth, analytic continuation, host equality,
quotient representatives, or a standard-model replacement.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_modulus\_budget\_totality}
\begin{proof}
Read the modulus coordinate through the modulus window exactness theorem
\autoref{thm:critical-line-witness-modulus-window-exactness}. Each depth
request is exhausted by the displayed $\NatUp$ depth input to $M$, the
$\RealUp$ row $R$, the $\RatUp$ comparison ledger $Q$, and the replay route
through $H,C,P,N$.

Combine this with the modulus refusal exhaustion theorem
\autoref{thm:critical-line-witness-modulus-refusal-exhaustion}. Zero-strip
modulus requests remain inside the same finite route and cannot become
analytic continuation evidence, zero-free-strip evidence, a global zero
classifier, or a host numeric oracle.

Finally apply the root bridge readback totality theorem
\autoref{thm:critical-line-witness-root-bridge-readback-totality} and the
root packet carrier theorem
\autoref{thm:critical-line-witness-root-zero-modulus-carrier}. They exhaust
public readback by the displayed packet rows $Z,S,M,R,Q,H,C,P,N$ before any
critical-line witness can be exported, with no route to $\mathsf{RH}$ truth,
host equality, quotient representatives, analytic continuation, or
standard-model replacement.
\end{proof}
