\begin{theorem}[Critical-line witness root classifier readiness]
\label{thm:critical-line-witness-root-classifier-readiness}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ root
packet. The root classifier is ready exactly on the displayed finite
$\BHist$ route through the source row $Z$, strip row $S$, transport row $H$,
continuation row $C$, provenance row $P$, and local
$\NameCert_{\CriticalLineWitnessUp}$ row $N$. Componentwise $\hsame$ transport
and $\Cont$ replay preserve that classifier surface, while $\Pkg$ provenance
records it as part of the same accepted packet. No host zero search,
analytic-continuation certificate, quotient representative, ambient
completeness witness, or proof of $\mathsf{RH}$ supplies an alternate
classifier.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_classifier\_readiness}
\begin{proof}
Project the root source and zero-strip rows already exposed by the carrier and
root source files. The source row $Z$ and strip row $S$ are the classifier
inputs before any downstream read is available.

Use the root source, modulus, and zero-strip obligation rows from the sibling
files. They bind the classifier to the displayed $\BHist$ packet and preserve
it under $\hsame$ transport and $\Cont$ replay along $H$ and $C$.

Finally attach the package and local name. The refusal and downstream-readback
rows keep host zero search, analytic continuation, quotient representatives,
ambient completeness, and $\mathsf{RH}$ proof objects outside the accepted
route, so the classifier is ready precisely on $Z,S,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness root ledger readiness]
\label{thm:critical-line-witness-root-ledger-readiness}
For an accepted $\CriticalLineWitnessUp$ root packet
$W=(Z,S,M,R,Q,H,C,P,N)$, the modulus and comparison ledger is ready exactly
through $M,R,Q,H,C,P,N$. The row $M$ supplies the root modulus budget, $R$
supplies the consumed real-part row, $Q$ supplies the rational comparison
ledger, $H$ records componentwise $\hsame$ transport, $C$ records the
displayed $\Cont$ route, $P$ records $\Pkg$ provenance, and $N$ records the
local $\NameCert$ row. The ledger has no accepted coordinate for host
comparison, quotient equality, analytic continuation, ambient completeness, or
an $\mathsf{RH}$ certificate.
\end{theorem}
\begin{proof}
Read the modulus rows first. The sibling root modulus and zero-strip package
files display $M$ as the finite budget through which the strip source can be
consumed.

Next read the comparison rows. The existing downstream-readback and classifier
ledger files attach $R$ and $Q$ to the same route and keep them stable under
the displayed $\hsame$ transport and $\Cont$ replay.

The package row and local name then close the ledger surface. Because the
refusal rows exclude host comparisons, quotient equality, analytic
continuation, ambient completeness, and $\mathsf{RH}$ proof data, every
accepted ledger read is the finite route $M,R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness root consumer readiness]
\label{thm:critical-line-witness-root-consumer-readiness}
Every root consumer of an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$ is ready on the combined source, classifier, ledger,
and naming surface
$$
Z,S,M,R,Q,H,C,P,N .
$$
The consumer reads this surface through the displayed $\BHist$ carrier,
componentwise $\hsame$ row, $\Cont$ route, $\Pkg$ provenance, and local
$\NameCert$ row. It cannot request a hidden zero source, off-packet modulus,
global zero classifier, analytic-continuation certificate, quotient
representative, ambient completeness theorem, or proof of $\mathsf{RH}$.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_consumer\_readiness\_certificate}
\begin{proof}
First combine the source and classifier surfaces. The displayed source,
zero-strip, and refusal rows make $Z,S,H,C,P,N$ the only classifier-ready root
route.

Next combine the modulus and ledger surfaces. The modulus, real-part, and
rational-comparison rows make $M,R,Q,H,C,P,N$ the only ledger-ready route for
downstream reads.

Finally intersect the two routes at the shared structural rows. Both are
carried by the same $\BHist$ packet, transported by the same $\hsame$ row,
replayed by the same $\Cont$ route, recorded by the same $\Pkg$ provenance,
and named by the same local $\NameCert$ row. The refusal and
downstream-readback siblings exclude every off-packet analytic, quotient,
completeness, zero-search, and $\mathsf{RH}$ demand, so the root consumer is
ready exactly on $Z,S,M,R,Q,H,C,P,N$.
\end{proof}
