\begin{theorem}[Critical-line witness root source coverage]
\label{thm:critical-line-witness-root-source-coverage}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet.
Every accepted source read exposed by $W$ is covered by the supplied
$\ZetaZerosUp$ row $Z$, the $\CritStripUp$ row $S$, the $\NatUp$ depth row $M$,
the $\RealUp$ real-part row $R$, the $\RatUp$ comparison row $Q$, and the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert_{\CriticalLineWitnessUp}$ structure carried by $H,C,P,N$. No source
read adds an analytic-continuation certificate, quotient representative, host
equality, ambient completeness row, or proof of $\mathsf{RH}$.
\end{theorem}
\begin{proof}
Project the accepted packet through the carrier surface. The root source triad
of \autoref{thm:critical-line-witness-root-source-triad} exposes the supplied
zero row, critical-strip row, and source-facing rational comparison row as
finite data before any downstream consumer reads $W$.

Next attach the remaining carrier projections. The root comparison ledger
\autoref{thm:critical-line-witness-root-comparison-ledger} accounts for
$M,R,Q,H,C,P,N$, while the zeta dependency lattice
\autoref{thm:critical-line-witness-zeta-link} places the zeta-facing source row
on the existing $\ZetaZerosUp$ boundary rather than on a new analytic object.

The structural rows are therefore exactly the visible $\BHist$ carrier,
componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance,
and local $\NameCert$ row. The root refusal route then removes analytic
continuation, quotient representatives, host equality, ambient completeness,
and $\mathsf{RH}$ proof content from the source surface.
\end{proof}

\begin{theorem}[Critical-line witness modulus-comparison transport stability]
\label{thm:critical-line-witness-modulus-comparison-transport-stability}
For an accepted $\CriticalLineWitnessUp$ packet
$W=(Z,S,M,R,Q,H,C,P,N)$, every modulus or rational-comparison route remains
stable under componentwise $\hsame$ transport through the displayed
$H,C,P,N$ rows. The transported route still reads only the $\NatUp$ depth row,
the $\RealUp$ real-part row, the $\RatUp$ comparison ledger, the finite
$\BHist$ carrier, displayed $\Cont$ replay, $\Pkg$ provenance, and local
$\NameCert$ row; it cannot import an external modulus source, analytic
estimate, quotient equality, host equality, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_modulus\_comparison\_transport\_stability}
\begin{proof}
Start with the root comparison ledger
\autoref{thm:critical-line-witness-root-comparison-ledger}. It places every
comparison read on $M,R,Q,H,C,P,N$, so the comparison has no coordinate outside
the accepted packet.

Now apply the root modulus ledger scope
\autoref{thm:critical-line-witness-root-modulus-ledger-scope}. This fixes the
modulus and rational-comparison surface as the complete root-facing ledger
before any transport is replayed by $\Cont$ or recorded by $\Pkg$ and
$\NameCert$.

Finally use the finite-budget ledger stability row
\autoref{thm:critical-line-witness-root-finite-budget-ledger-stability}. It
identifies componentwise $\hsame$ transport as preservation of the same
displayed finite ledger, while the refusal ledger excludes analytic estimates,
quotient equality, host equality, ambient completeness, and any off-packet
modulus source.
\end{proof}

\begin{theorem}[Critical-line witness root refusal-boundary totality]
\label{thm:critical-line-witness-root-refusal-boundary-totality}
Every $\mathsf{RH}$-facing or zeta-facing consumer of the source and transport
surface of an accepted $\CriticalLineWitnessUp$ packet receives only the finite
refusal boundary over
$$
Z,S,M,R,Q,H,C,P,N.
$$
The consumer may read the supplied $\ZetaZerosUp$ and $\CritStripUp$ rows, the
$\NatUp$, $\RealUp$, and $\RatUp$ comparison surface, and the displayed
$\BHist/\hsame/\Cont/\Pkg/\NameCert$ structure. It receives no proof of
$\mathsf{RH}$, global zero classifier, analytic-continuation theorem, quotient
representative, host equality, ambient completeness row, or external zeta
object.
\end{theorem}
\begin{proof}
Begin with RH-refusal ledger completeness,
\autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. It already
classifies requests for $\mathsf{RH}$ proof data, global zero classification,
analytic continuation, quotient representatives, host equality, and ambient
completeness as refusal-side reads of the displayed packet.

Use the root RH-boundary refusal
\autoref{thm:critical-line-witness-root-rh-boundary-refusal} together with the
zeta-consumer non-escape row
\autoref{thm:critical-line-witness-zeta-consumer-nonescape}. The first keeps
RH-facing requests on the finite refusal boundary, and the second prevents
zeta-facing consumers from replacing the displayed packet by completed zeta
data or an analytic continuation route.

Finally apply the RH-boundary refusal exhaustion row
\autoref{thm:critical-line-witness-rh-boundary-refusal-exhaustion}. The source
coverage and transport stability rows above account for every positive
coordinate still readable by the consumer, so all remaining RH- or zeta-facing
demands are total as refusals on $Z,S,M,R,Q,H,C,P,N$ and nowhere else.
\end{proof}
