\begin{theorem}[Critical-line witness modulus comparison route totality]
\label{thm:critical-line-witness-modulus-comparison-route-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Every modulus comparison route of $W$ factors through the displayed modulus row $M$, real-part row $R$, rational comparison ledger $Q$, transport row $H$, continuation row $C$, package row $P$, and local $\NameCert$ row $N$. No comparison route reads a global zero classifier, host equality, quotient representative, analytic-continuation certificate, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with the modulus request factorization of \autoref{thm:critical-line-witness-modulus-request-factorization}. It places each comparison request on the displayed $\Cont$ route before the public read of $M$ and keeps the request inside $R,Q,H,C,P,N$.

Then use the strip-modulus ledger triad of \autoref{thm:critical-line-witness-strip-modulus-ledger-triad}. The strip row, modulus request row, and rational comparison ledger are one finite BEDC-visible triad under the same transport, continuation, package, and naming rows.

Finally apply the obligation closure package of \autoref{thm:critical-line-witness-obligation-closure-package}. The available obligation surface is exactly the carrier, naming, transport, continuation, package, non-escape, and ledger rows, so every modulus comparison route is total through $M,R,Q,H,C,P,N$.
\end{proof}

\begin{theorem}[Critical-line witness supplied zero-strip transport lock]
\label{thm:critical-line-witness-supplied-zero-strip-transport-lock}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The supplied zero row $Z$ and critical-strip row $S$ remain locked to the displayed $\BHist$ surface by the componentwise $\hsame$ transport row $H$, together with $C,P,N$. They cannot be replaced by host equality, zero search, a global zero-set classifier, quotient identification, or analytic continuation.
\end{theorem}
\begin{proof}
Project the supplied input carrier row of \autoref{thm:critical-line-witness-supplied-input-carrier-row}. The rows $Z$ and $S$ are input coordinates of the accepted packet, while modulus and comparison rows are read only after those supplied rows are exposed.

Next use supplied zero readback from \autoref{thm:critical-line-witness-supplied-zero-readback} and strip-zero compatibility from \autoref{thm:critical-line-witness-strip-zero-compatibility}. These rows identify the zero-facing and strip-facing routes with the displayed $\BHist$ packet and its $\hsame$ transport.

The downstream refusal package of \autoref{thm:critical-line-witness-downstream-refusal-package} supplies the non-escape clause. It excludes host equality, zero search, global zero classification, quotient representatives, analytic continuation, and ambient completeness, so the zero-strip pair remains locked by the displayed transport route.
\end{proof}

\begin{theorem}[Critical-line witness RH-refusal ledger completeness]
\label{thm:critical-line-witness-rh-refusal-ledger-completeness}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The refusal ledger of $W$ is complete for excluding an $\mathsf{RH}$ proof, a global zero classifier, an analytic-continuation certificate, a quotient representative, and ambient completeness from every downstream read. Downstream consumers can cite only $Z,S,M,R,Q,H,C,P,N$ and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_rh\_refusal\_ledger\_completeness}
\begin{proof}
Begin with the RH consumer boundary package of \autoref{thm:critical-line-witness-rh-consumer-boundary-package}. It packages downstream access as the zero-source route, strip-modulus ledger triad, nonproof boundary, refusal row, and local obligation surface.

Use downstream source obligation from \autoref{thm:critical-line-witness-downstream-source-obligation}. It factors every RH-facing downstream source read through the finite supplied-zero and modulus packet $Z,S,M,R,Q,H,C,P,N$.

Finally apply downstream refusal package from \autoref{thm:critical-line-witness-downstream-refusal-package} and ledger non-escape obligation from \autoref{thm:critical-line-witness-ledger-nonescape-obligation}. These rows exclude $\mathsf{RH}$ proof data, global zero classification, analytic continuation, quotient representatives, host equality, and ambient completeness from the ledger, so the refusal surface is complete for the listed downstream exclusions.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip carrier totality]
\label{thm:critical-line-witness-zero-strip-carrier-totality}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The root carrier of $W$ is total exactly over the supplied zero row $Z$, critical-strip row $S$, modulus row $M$, real-part row $R$, rational comparison ledger $Q$, and structural rows $H,C,P,N$. It has no coordinate for an $\mathsf{RH}$ proof, global zero classifier, analytic-continuation certificate, quotient representative, host equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:critical-line-witness-modulus-comparison-route-totality}. It places every modulus and rational comparison read inside $M,R,Q,H,C,P,N$ and excludes analytic, quotient, host-equality, and completeness coordinates from the comparison route.

Next use \autoref{thm:critical-line-witness-supplied-zero-strip-transport-lock}. The supplied zero row $Z$ and critical-strip row $S$ remain locked to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route.

The root-source triad of \autoref{thm:critical-line-witness-root-source-triad} and the root comparison ledger of \autoref{thm:critical-line-witness-root-comparison-ledger} assemble the carrier rows visible to downstream consumers. Finally \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness} removes every requested $\mathsf{RH}$ proof, global zero classifier, analytic-continuation certificate, quotient representative, host equality, and ambient completeness coordinate not displayed in $W$.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_zero\_strip\_carrier\_totality}

\begin{theorem}[Critical-line witness zero-strip classifier transport]
\label{thm:critical-line-witness-zero-strip-classifier-transport}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. Any replacement of the supplied zero-strip classifier pair must transport through the same componentwise $\hsame$ row $H$, displayed $\Cont$ row $C$, $\Pkg$ row $P$, and local $\NameCert$ row $N$. Such a replacement cannot substitute a host zero-search, global zero-set classifier, analytic-continuation certificate, quotient representative, host equality, or ambient completeness coordinate for $Z,S$.
\end{theorem}
\begin{proof}
Start with \autoref{thm:critical-line-witness-supplied-zero-strip-transport-lock}. It binds the rows $Z,S$ to the displayed componentwise transport route and prevents their replacement by host equality, zero search, quotient identification, or analytic continuation.

Use \autoref{thm:critical-line-witness-root-source-triad}. The zero-strip pair is part of the finite source triad seen by downstream readers, and the triad is carried only through $H,C,P,N$.

Now apply the root comparison ledger of \autoref{thm:critical-line-witness-root-comparison-ledger} and the RH-refusal ledger completeness of \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. The comparison and refusal rows leave no public slot from which a replacement classifier could import a host zero search, analytic certificate, quotient representative, host equality, or ambient completeness witness.
\end{proof}

\begin{theorem}[Critical-line witness RH refusal non-escape]
\label{thm:critical-line-witness-rh-refusal-nonescape}
Every $\mathsf{RH}$-facing downstream read of an accepted $\CriticalLineWitnessUp$ packet factors through the finite refusal route over $Z,S,M,R,Q,H,C,P,N$. The read exports only the displayed refusal ledger: it does not export an $\mathsf{RH}$ proof, a zero-set classifier, a host zero-search route, an analytic-continuation certificate, a quotient representative, host equality, or ambient completeness.
\end{theorem}
\begin{proof}
First apply \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. It already exhausts downstream $\mathsf{RH}$-facing access by the displayed rows $Z,S,M,R,Q,H,C,P,N$ and by the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ structure.

Then combine \autoref{thm:critical-line-witness-modulus-comparison-route-totality} with \autoref{thm:critical-line-witness-supplied-zero-strip-transport-lock}. The comparison side must read $M,R,Q,H,C,P,N$, while the zero-strip side must read $Z,S,H,C,P,N$.

Finally use \autoref{thm:critical-line-witness-root-source-triad} and \autoref{thm:critical-line-witness-root-comparison-ledger}. Together they identify the root-facing source and comparison rows as one finite refusal package, with no exported proof of $\mathsf{RH}$ and no exported zero-set classifier.
\end{proof}

\begin{theorem}[Critical-line witness root source triad]
\label{thm:critical-line-witness-root-source-triad}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The supplied zero row $Z$, the critical-strip row $S$, and the rational comparison ledger $Q$ are exposed as one finite $\BHist$ source triad before any downstream boundary may read the packet. The triad is carried only through the displayed transport row $H$, continuation row $C$, package row $P$, and local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:critical-line-witness-carrier}. Its accepted packet has $Z$, $S$, and $Q$ as displayed rows, so the root-facing source data are already finite $\BHist$ coordinates rather than host zero data or analytic structure.

Apply \autoref{thm:critical-line-witness-namecert-obligations}. The local naming row requires the carrier, classifier, transport, package, and ledger obligations to be discharged on the same visible packet.

Finally combine \autoref{thm:critical-line-witness-modulus-comparison-route-totality} with \autoref{thm:critical-line-witness-supplied-zero-strip-transport-lock}. The comparison ledger is total through the displayed modulus and rational comparison rows, while the zero and strip rows stay locked to $H,C,P,N$. Hence $Z,S,Q$ form the finite source triad available to downstream boundary chapters.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_source\_triad}

\begin{theorem}[Critical-line witness root comparison ledger]
\label{thm:critical-line-witness-root-comparison-ledger}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, every root-facing rational comparison used by a downstream consumer factors through the finite ledger $Q$ together with $M,R,H,C,P,N$. The comparison route does not read a global zero set, a quotient representative, analytic continuation, or an ambient completeness principle.
\end{theorem}
\begin{proof}
Start with the modulus comparison route totality of \autoref{thm:critical-line-witness-modulus-comparison-route-totality}. It places every comparison request on the displayed modulus, real-part, rational comparison, transport, continuation, package, and naming rows.

Use \autoref{thm:critical-line-witness-namecert-obligations} to bind that comparison route to the local carrier and ledger obligations. The obligation surface is finite and names only the accepted packet coordinates.

The supplied zero-strip transport lock of \autoref{thm:critical-line-witness-supplied-zero-strip-transport-lock} prevents the comparison route from being replaced by a host zero search, quotient representative, analytic continuation certificate, or ambient completeness row. Thus the root-facing comparison ledger is exactly the displayed finite route through $Q$.
\end{proof}

\begin{theorem}[Critical-line witness root refusal route]
\label{thm:critical-line-witness-root-refusal-route}
The root-facing route of an accepted $\CriticalLineWitnessUp$ packet refuses every downstream request for an $\mathsf{RH}$ proof, zero search, global zero classifier, analytic-continuation certificate, quotient representative, host equality, or ambient completeness witness. A downstream chapter may cite only the finite source triad $Z,S,Q$ and the displayed rows $M,R,H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with the root source triad of \autoref{thm:critical-line-witness-root-source-triad}. It exposes the supplied zero row, critical-strip row, and rational comparison ledger as finite $\BHist$ rows under the same transport and naming surface.

Next use the root comparison ledger of \autoref{thm:critical-line-witness-root-comparison-ledger}. It forces every rational comparison read through the displayed $Q$ route and rules out analytic and quotient replacements.

Finally apply \autoref{thm:critical-line-witness-rh-refusal-ledger-completeness}. The refusal ledger already excludes $\mathsf{RH}$ proof data, zero classification, analytic continuation, quotient representatives, host equality, and ambient completeness, so the root-facing route is a finite refusal package rather than an analytic proof surface.
\end{proof}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_root\_refusal\_route}
