\begin{theorem}[Critical-line witness scoped source boundary]
\label{thm:critical-line-witness-scoped-source-boundary}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The scoped source boundary of $W$ is the finite surface
$$
Z,S,M,R,Q,H,C,P,N.
$$
Here $Z$ is the supplied $\ZetaZerosUp$ row, $S$ is the supplied $\CritStripUp$ row, $M$ is the $\NatUp$ depth-request row, $R$ is the $\RealUp$ real-part row, $Q$ is the $\RatUp$ comparison ledger, and the accepted packet itself is the finite $\BHist$ carrier surface with $H,C,P,N$ as the $\hsame$ row, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The boundary supplies no proof of $\mathsf{RH}$, zero search, host equality, quotient representative, analytic continuation, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_scoped\_source\_boundary}
\begin{proof}
Start with the root zero-strip route and the zero-strip depth lock. They expose the supplied $Z$ and $S$ rows before any modulus read and keep the subsequent $\NatUp$ depth request on the displayed route through $H,C,P,N$.

Next attach the modulus and comparison rows. The root modulus ledger, comparison-window totality, and root comparison ledger force every request through $M,R,Q$ under the same finite transport, continuation, provenance, and local naming surface.

Finally apply the RH-boundary downstream lock and the root non-escape package. These rows identify the export as a finite witness boundary and remove $\mathsf{RH}$ proof data, zero search, host equality, quotient representatives, analytic continuation, and ambient completeness from the source surface.
\end{proof}

\begin{theorem}[Critical-line witness source ledger exhaustion]
\label{thm:critical-line-witness-source-ledger-exhaustion}
Every downstream source-ledger read of an accepted $\CriticalLineWitnessUp$ packet factors through the single finite route
$$
Z,S,M,R,Q,H,C,P,N.
$$
The read may consume the supplied zero row, supplied critical-strip row, natural depth row, real-part row, rational comparison ledger, displayed history row, componentwise transport, continuation replay, package provenance, and local naming row, and it has no second source ledger outside that route.
\end{theorem}
\begin{proof}
First use the scoped source boundary. It names the finite route and records which rows can appear in a downstream source-ledger read.

Then compose the root carrier projection with the root refusal consumer exactness theorem. The projection shows that downstream root evidence is exactly the displayed packet, and exactness prevents the consumer from treating any host object as an additional source.

The refusal ledger completeness theorem closes the route. Since the packet refuses $\mathsf{RH}$ proof data, zero search, global zero classification, host equality, quotient representatives, analytic continuation, and ambient completeness, the displayed route exhausts the source ledger.
\end{proof}

\begin{theorem}[Critical-line witness zero-strip modulus source totality]
\label{thm:critical-line-witness-zero-strip-modulus-source-totality}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, every source read that begins with the supplied zero-strip rows $Z,S$ and later asks for a modulus or comparison row is total through
$$
Z,S,M,R,Q,H,C,P,N.
$$
The total route binds the $\ZetaZerosUp$ row, $\CritStripUp$ row, $\NatUp$ depth requests, $\RealUp$ real-part row, $\RatUp$ comparison ledger, $\BHist$ evidence, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and $\NameCert$ row without adding RH proof content, zero search, host equality, quotient representatives, analytic continuation, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the supplied zero-strip route. It makes $Z,S,H,C,P,N$ the entry surface for zero-strip reads and prevents replacement by analytic or host-level data.

Next use the zero-strip depth lock and root modulus ledger. The first theorem forces later modulus requests to stay attached to the same zero-strip route, while the second theorem records those requests through $M,R,Q,H,C,P,N$.

Finally combine source-ledger exhaustion with the RH-boundary downstream lock. The downstream read therefore has one finite route through $Z,S,M,R,Q,H,C,P,N$ and no exit to $\mathsf{RH}$ proof data, zero search, host equality, quotient representatives, analytic continuation, or ambient completeness.
\end{proof}
