\begin{theorem}[Critical-line witness scoped source lock]
\label{thm:critical-line-witness-scoped-source-lock}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The scoped source lock of $W$ is the finite route through the supplied $\ZetaZerosUp$ row $Z$, supplied $\CritStripUp$ row $S$, $\RealUp$ real-part row $R$, $\RatUp$ comparison ledger $Q$, accepted $\BHist$ carrier surface, componentwise $\hsame$ row $H$, $\Cont$ replay row $C$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $N$. Every source read for $W$ is bound to those rows and cannot be replaced by host equality, a global zero-set classifier, analytic continuation, quotient representation, or ambient completeness.
\end{theorem}
\begin{proof}
Start with carrier admission for the accepted packet. The carrier exposes $Z,S,M,R,Q,H,C,P,N$ as the available finite rows and gives no coordinate for host equality, quotient data, analytic continuation, or ambient completeness.

Use zero-strip compatibility to bind $Z$ and $S$ to the same supplied source over $\ZetaZerosUp$ and $\CritStripUp$. Transport then occurs only through the displayed $\BHist$ and $\hsame$ rows, and continuation reads occur only through $C$.

Finally apply the modulus comparison route totality and RH-refusal ledger completeness. They attach $R,Q,P,N$ to the same route and exclude global zero classification and $\mathsf{RH}$ proof data from the source surface.
\end{proof}

\begin{theorem}[Critical-line witness scoped ledger exactness]
\label{thm:critical-line-witness-scoped-ledger-exactness}
Let $W=(Z,S,M,R,Q,H,C,P,N)$ be an accepted $\CriticalLineWitnessUp$ packet. The ledger exactness surface for $W$ consists exactly of the modulus row $M$, the $\RealUp$ row $R$, the $\RatUp$ comparison ledger $Q$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows $H,C,P,N$. Any downstream comparison or modulus consumer must factor through that surface after reading the supplied $\ZetaZerosUp$ and $\CritStripUp$ rows $Z,S$.
\end{theorem}
\begin{proof}
Project the modulus and comparison rows from the carrier. The modulus row $M$, real-part row $R$, and rational comparison ledger $Q$ are displayed coordinates of the same accepted packet.

Apply the modulus comparison route totality. It forces comparison reads through $M,R,Q,H,C,P,N$ and makes the route total without adding a hidden numeric oracle, host real equality, quotient representative, or analytic-continuation certificate.

The root comparison ledger then supplies exactness for downstream consumers. Together with the scoped source lock, the comparison surface is the finite ledger following the supplied $Z,S$ source rows and no second ledger is available.
\end{proof}

\begin{theorem}[Critical-line witness scoped nonescape boundary]
\label{thm:critical-line-witness-scoped-nonescape-boundary}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, the scoped nonescape boundary is the refusal row generated by the same $\ZetaZerosUp$, $\CritStripUp$, $\RealUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ dependencies. It permits downstream use of the finite source lock and ledger exactness, but it exports no $\mathsf{RH}$ proof, no zero search, no global zero classifier, no host equality, no quotient representative, no analytic-continuation certificate, and no ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with the scoped source lock. It identifies the only source dependencies available to a downstream consumer as $Z,S,R,Q,H,C,P,N$ together with the accepted packet row.

Use scoped ledger exactness for every modulus or comparison read. The ledger route stays inside $M,R,Q,H,C,P,N$ and therefore cannot become an independent analytic or quotient route.

Finally invoke RH-refusal ledger completeness and the root refusal route. These refusal rows already cover $\mathsf{RH}$ proof data, zero search, global zero classification, host equality, quotient representatives, analytic continuation, and ambient completeness, so the scoped boundary is closed under the stated nonescape obligations.
\end{proof}
