The $\CriticalLineWitnessUp$ sibling-dependency route is read only after the zeta source, zero-locus witness, and analytic-continuation boundary have already been displayed by sibling chapters. The zeta source surface of \autoref{ch:concrete-instances-zeta-basic-namecert} supplies the finite $\ZetaUp$ row, the zero-side witness rows are supplied by \autoref{ch:concrete-instances-zeta-zeros-namecert}, and the continuation boundary is supplied by \autoref{ch:concrete-instances-zeta-continuation}. The local witness packet therefore consumes those rows through its displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support before any critical-line consumer reads a witness route.

\begin{lemma}[CriticalLineWitness sibling dependency route]
\label{lem:critical-line-witness-sibling-dependency-route}
Every accepted $\CriticalLineWitnessUp$ route that exports a critical-line witness read is supported by the displayed $\ZetaUp$ source row, the zero-locus witness row, and the analytic-continuation boundary row already present in sibling chapters. The route exports no independent RH proof, global zero classifier, analytic-continuation primitive, quotient representative, host equality, or ambient completeness theorem.
\end{lemma}
\begin{proof}
First read the zeta source through \autoref{ch:concrete-instances-zeta-basic-namecert}. This supplies the source row before the local critical-line witness classifier is consulted.

Next read the zero-locus and continuation rows through \autoref{ch:concrete-instances-zeta-zeros-namecert} and \autoref{ch:concrete-instances-zeta-continuation}. These rows provide the zero-facing and boundary data consumed by the local witness packet.

Finally project the local $\CriticalLineWitnessUp$ support. Its $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows transport and replay the sibling data, but they do not add an RH proof, global zero classifier, analytic-continuation primitive, quotient representative, host equality, or ambient completeness coordinate.
\end{proof}
