\begin{theorem}[Critical-line witness terminal zero-source totality]
\label{thm:critical-line-witness-terminal-zero-source-totality}
Every terminal critical-line read from an accepted $\CriticalLineWitnessUp$ packet first exposes the supplied zero-source row $Z$ together with the supplied critical-strip row $S$ and the displayed route rows $H,C,P,N$. The terminal read may continue to the modulus and comparison rows only after this zero-source surface is present; it cannot begin from a zero search, global zero classifier, host complex equality, quotient representative, analytic-continuation certificate, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessCarrier\_terminal\_zero\_source\_totality}
\begin{proof}
Project the carrier of \autoref{def:critical-line-witness-carrier}. The supplied zero row $Z$ and supplied strip row $S$ are visible before any modulus coordinate can be read.

Use the root zero-strip route of \autoref{thm:critical-line-witness-root-zero-strip-route} and the zero-row source scope of \autoref{thm:critical-line-witness-zero-row-scope}. These results force the first terminal read through $Z,S,H,C,P,N$.

Finally apply the root zero-strip exclusion of \autoref{thm:critical-line-witness-root-zero-strip-exclusion}. It removes zero search, host equality, quotient representatives, analytic continuation, and ambient completeness from the terminal source route.
\end{proof}

\begin{theorem}[Critical-line witness terminal modulus-comparison scope]
\label{thm:critical-line-witness-terminal-modulus-comparison-scope}
For an accepted $\CriticalLineWitnessUp$ packet $W=(Z,S,M,R,Q,H,C,P,N)$, every terminal modulus comparison is scoped to the displayed $\RatUp$, $\RealUp$, and $\ZetaZerosUp$ rows together with the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ routes. The comparison route is exactly the packet surface $Z,S,M,R,Q,H,C,P,N$, and it exports no external real-order decision, host equality, quotient real representative, hidden numeric oracle, or analytic completeness principle.
\end{theorem}
\begin{proof}
First expose the supplied zero-source rows using \autoref{thm:critical-line-witness-terminal-zero-source-totality}. The terminal comparison is attached to the displayed $\ZetaZerosUp$ and $\CritStripUp$ source rows before it reaches any modulus data.

Next apply the root modulus ledger scope of \autoref{thm:critical-line-witness-root-modulus-ledger-scope}. It exhausts modulus and rational-comparison reads by $M,R,Q,H,C,P,N$.

Finally combine the rational comparison ledger exactness of \autoref{thm:critical-line-witness-rat-comparison-ledger-exactness} with the non-escape boundary of \autoref{thm:critical-line-witness-nonescape-boundary}. Thus the terminal comparison stays inside the displayed $\RatUp$, $\RealUp$, $\ZetaZerosUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{proof}

\begin{theorem}[Critical-line witness terminal RH-refusal exactness]
\label{thm:critical-line-witness-terminal-rh-refusal-exactness}
Every terminal RH-facing read of an accepted $\CriticalLineWitnessUp$ packet exports only the finite critical-line witness boundary
$$
Z,S,M,R,Q,H,C,P,N.
$$
It refuses $\mathsf{RH}$ proof content, universal zero classification, zero-producing search, host complex equality, quotient real equality, selected Cauchy representatives, analytic-continuation certificates, and ambient analytic completeness.
\end{theorem}
\begin{proof}
Begin with the terminal zero-source totality theorem. It makes the supplied zero and strip rows the first visible source of the terminal read.

Then use the terminal modulus-comparison scope theorem. The modulus and rational comparison side is exhausted by the displayed $\RealUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Finally apply the root RH-boundary refusal of \autoref{thm:critical-line-witness-root-rh-boundary-refusal}. The terminal packet is therefore a finite critical-line witness boundary, not an $\mathsf{RH}$ proof surface or an analytic oracle.
\end{proof}
