The $\CriticalLineWitnessUp$ root package is a witness surface over existing zeta and RH boundary rows, not an independent zeta-function object. Its zero-strip and critical-line reads consume the $\ZetaZerosUp$ sibling surface and the RH horizon before any modulus witness is public.

\begin{theorem}[Critical-line witness zeta dependency lattice]
\label{thm:critical-line-witness-zeta-link}
Every $\CriticalLineWitnessUp$ zero-strip or critical-line read consumes the $\ZetaZerosUp$ zero-count surface of \autoref{ch:concrete-instances-zeta-zeros-namecert} or the RH-boundary surface of \autoref{ch:visions-riemann-hypothesis} before it can expose a modulus witness. The packet supplies a finite witness surface through $Z,S,M,R,Q,H,C,P,N$; it does not construct a separate zeta-function object, zero oracle, or proof of $\mathsf{RH}$.
\end{theorem}
\leanchecked{BEDC.Derived.CriticalLineWitnessUp.CriticalLineWitnessZetaLink}
\begin{proof}
Start with the root source package already displayed by the hub. The supplied zero row $Z$ and critical-strip row $S$ enter through the root zero-strip route, while $M,R,Q$ remain the later modulus and rational-comparison surface.

Apply \autoref{thm:critical-line-witness-root-zero-strip-route} and \autoref{thm:critical-line-witness-root-zero-carrier}. These sibling rows project the zero-strip and critical-line data to the existing $\ZetaZerosUp$ and critical-strip boundary before any modulus read is exposed.

Next use \autoref{thm:critical-line-witness-rh-nonescape-package} and \autoref{thm:critical-line-witness-zero-strip-consumer-boundary}. They place downstream RH-facing and zero-count consumers behind the same finite route and explicitly refuse zero search, analytic-continuation export, host equality, quotient representatives, and an RH proof.

It remains only to read the modulus witness. By \autoref{thm:critical-line-witness-root-modulus-ledger}, such a read passes through $M,R,Q,H,C,P,N$ after the zero-strip and RH boundary rows have been supplied. Hence $\CriticalLineWitnessUp$ records a dependency lattice over the zeta and RH siblings, not a standalone zeta-function certificate.
\end{proof}
