The $\CriticalLineWitnessUp$ continuation lattice reads critical-line data only after the displayed $\ZetaContinuationWitnessUp$ source-lock rows have been exposed. This places the local witness behind the continuation, pole, functional-equation, trivial-zero, Gamma-boundary, transport, replay, provenance, and naming surface of \autoref{ch:concrete-instances-zeta-continuation-witness-namecert}.

\begin{theorem}[CriticalLineWitness Zeta continuation route]
\label{thm:critical-line-witness-zeta-continuation-route}
Every $\CriticalLineWitnessUp$ read offered to a zero-strip consumer must first pass through the $\ZetaContinuationWitnessUp$ continuation route of \autoref{ch:concrete-instances-zeta-continuation-witness-namecert}. In particular, the read displays the continuation row, pole ledger, functional-equation row, trivial-zero ledger, Gamma-boundary row, componentwise transport, replay, provenance, and local $\NameCert$ rows before any zero-strip consumer sees the witness as critical-line data. The route supplies no RH proof, global zero classifier, hidden analytic branch, completed Gamma certificate, host equality of zeta functions, or selected representative outside those rows.
\end{theorem}
\begin{proof}
Start with the displayed $\ZetaContinuationWitnessUp$ packet. Its source-lock surface exposes the continuation, pole, functional-equation, trivial-zero, and Gamma-boundary rows together with transport, replay, provenance, and local naming data.

The $\CriticalLineWitnessUp$ consumer can then read only the continuation rows named by that packet. The witness is therefore downstream from the zeta-continuation surface, not parallel to it.

Finally inspect the excluded data. Since no RH proof, global zero classifier, hidden analytic branch, completed Gamma certificate, host equality of zeta functions, or selected representative is a coordinate of the source-lock packet, the zero-strip consumer cannot receive any of those objects through the critical-line witness route.
\end{proof}
