\begin{theorem}[RegSeqRat finite-request source section]
\label{thm:regseqrat-finite-request-source-section}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a public finite
request to the accepted packet. Then $S$ factors through one displayed
$\RegSeqRatUp$ source section carried by a finite $\BHist$ packet. The visible
rows of that section are exactly the following rows:
\begin{enumerate}
\item the $\StreamNameUp$ schedule rows selected by the request;
\item the $\DyadicRatCoreUp$ endpoint, radius, and finite dyadic-distance rows
read at those schedule positions;
\item the $\RegSeqRatUp$ classifier row and the regularity rows certifying the
accepted packet;
\item the componentwise $\hsame$ rows tying the schedule, dyadic endpoint,
radius, distance, classifier, and regularity rows to the same request packet;
\item the displayed $\Cont$ routes from the StreamName schedule through the
dyadic rows and the RegSeqRat classifier surface;
\item the $\mathsf{Pkg}$ provenance over $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item the local $\NameCert_{\RegSeqRatUp}$ rows for the request.
\end{enumerate}
No other row is part of the RegSeqRat source section.
\end{theorem}
\leanchecked{BEDC.Derived.RegSeqRatUp.RegSeqRatFiniteRequestSourceSection}
\begin{proof}
Begin with the StreamName finite-observation section of
\autoref{thm:streamname-finite-observation-section}. It gives the displayed
schedule rows named by the finite request and places them in one finite source
packet.

Apply the RegSeqRat tail-budget section lock,
\autoref{thm:streamname-finite-observation-regseqrat-tail-budget-section-lock}.
The lock prevents the request from replacing the displayed schedule by an
off-packet tail selector, so every later RegSeqRat row is read over the same
finite window.

Next use the exact RegSeqRat handoff,
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. It supplies
the dyadic endpoint, radius, finite distance, classifier, and regularity rows
over the displayed schedule.

Now apply \autoref{thm:regseqrat-common-dyadic-tail-ledger}. The common ledger
identifies the componentwise $\hsame$ rows, $\Cont$ routes, package
provenance, and local naming rows as part of the same finite RegSeqRat packet.
This gives one $\BHist$ source section and no second source coordinate.
\end{proof}

\begin{theorem}[RegSeqRat Real request section nonescape]
\label{thm:regseqrat-real-request-section-nonescape}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a public finite
request to $R$ that is consumed by a $\RealUp$ seal. Then the same displayed
source section of
\autoref{thm:regseqrat-finite-request-source-section} is the entire source
section seen by the seal. In particular the section cannot export quotient
stream equality, host sequence equality, selected limits, ambient completeness,
metric-completeness data, choice data, or a second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
First factor the request through
\autoref{thm:regseqrat-finite-request-source-section}. The factorization has
only the StreamName schedule rows, DyadicRatCore endpoint, radius, and distance
rows, RegSeqRat classifier and regularity rows, and the displayed transport,
route, package, and local naming rows.

Apply the Real finite-request fusion theorem,
\autoref{thm:real-regseqrat-finite-request-fusion}. It says that a Real seal
which consumes the same request reads through one finite $\BHist$ packet with
the same schedule, dyadic, classifier, regularity, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and local $\NameCert$ rows.

Finally compare the two packets through
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness} and
\autoref{thm:regseqrat-common-dyadic-tail-ledger}. These theorems keep the
StreamName, DyadicRatCore, and RegSeqRat faces as the only source faces
available to the seal-facing request. Since those faces carry no row for
quotient stream equality, host sequence equality, selected limits, ambient
completeness, metric-completeness data, choice data, or a second Real seal
coordinate, the consumed section cannot export any such datum.
\end{proof}

\begin{theorem}[RegSeqRat finite-request Real seal correspondence]
\label{thm:regseqrat-finite-request-real-seal-correspondence}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a public finite
request to $R$ that is consumed by a $\RealUp$ seal. The finite request source
section of \autoref{thm:regseqrat-finite-request-source-section} determines
the seal-visible source section of
\autoref{thm:regseqrat-real-request-section-nonescape}: its rows restrict
exactly to the StreamName schedule, the $\DyadicRatCoreUp$ endpoint, radius,
and dyadic-distance rows, the $\RegSeqRatUp$ classifier and regularity rows,
the componentwise $\hsame$ rows, the displayed $\Cont$ routes, the
$\mathsf{Pkg}$ provenance, and the local $\NameCert_{\RegSeqRatUp}$ rows.
Conversely any seal-visible section for the same request restricts to exactly
those rows of the finite request source section. The correspondence carries no
quotient stream equality, host sequence equality, selected limits, ambient
completeness, metric-completeness data, choice data, or second seal coordinate.
\end{theorem}
\begin{proof}
First build the finite source packet with
\autoref{thm:regseqrat-finite-request-source-section}. This gives the unique
displayed request section whose visible rows are the StreamName schedule rows,
the dyadic endpoint, radius, and finite distance rows, the RegSeqRat classifier
and regularity rows, and the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
local $\NameCert$ rows.

Next route the same public request to the Real consumer by
\autoref{thm:real-regseqrat-finite-request-fusion}. The fusion theorem forces
the seal to read through the finite $\BHist$ packet already named by the
request, so the consumer has no independent source packet from which additional
rows could be drawn.

The common visible rows are then fixed by
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness} and
\autoref{thm:regseqrat-common-dyadic-tail-ledger}. These theorems identify the
schedule, dyadic, classifier, regularity, $\hsame$, $\Cont$, package, and
naming rows on both sides of the handoff, giving the restriction from the
finite source section to the seal-visible section.

For the converse, start with a seal-visible section for the same request and
apply \autoref{thm:regseqrat-real-request-section-nonescape}. Nonescape says
that the seal-visible section is already the displayed RegSeqRat finite source
section, so restricting it back along the request recovers exactly the same
StreamName schedule, dyadic endpoint, radius, distance, classifier,
regularity, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert$ rows.
The excluded rows are absent on both sides, so the correspondence introduces
no quotient stream equality, host sequence equality, selected limit, ambient or
metric completeness, choice datum, or second seal coordinate.
\end{proof}

\begin{theorem}[RegSeqRat finite-request terminal budget factorization]
\label{thm:regseqrat-finite-request-terminal-budget-factorization}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a public finite
request to $R$ that is consumed by a $\RealUp$ seal. Every terminal budget
consumer of the finite seal request factors through exactly the rows of the
finite request source section:
\begin{enumerate}
\item the $\StreamNameUp$ schedule rows selected by $S$;
\item the $\DyadicRatCoreUp$ endpoint, radius, and finite dyadic-distance rows
read at those schedule positions;
\item the $\RegSeqRatUp$ classifier row and regularity rows;
\item the componentwise $\hsame$ rows for the schedule, dyadic endpoint,
radius, distance, classifier, regularity, and seal-facing request packet;
\item the displayed $\Cont$ routes from the schedule through the dyadic rows,
classifier surface, regularity rows, and seal read;
\item the $\mathsf{Pkg}$ provenance over $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item the local $\NameCert_{\RegSeqRatUp}$ rows from the finite request source
section.
\end{enumerate}
The factorization exports no quotient stream equality, host real equality,
host sequence equality, selected limit, choice datum, ambient completeness
principle, metric-completeness datum, or second seal coordinate.
\end{theorem}
\begin{proof}
Start with the finite request source section of
\autoref{thm:regseqrat-finite-request-source-section}. It displays the
StreamName schedule, DyadicRatCore endpoint, radius, and distance rows,
RegSeqRat classifier and regularity rows, componentwise $\hsame$, displayed
$\Cont$, package provenance, and local RegSeqRat naming rows as one finite
$\BHist$ source section.

Next use the request nonescape theorem,
\autoref{thm:regseqrat-real-request-section-nonescape}. It says that a
$\RealUp$ seal consuming the same public finite request sees no source section
beyond those displayed rows, so quotient streams, host equality rows, selected
limits, completeness principles, choice data, and second seal coordinates
remain outside the request surface.

The correspondence theorem
\autoref{thm:regseqrat-finite-request-real-seal-correspondence} identifies
the seal-visible section with the finite request source section in both
directions. Thus any consumer that reaches the seal-facing request must first
restrict to the same StreamName, DyadicRatCore, RegSeqRat, transport, route,
provenance, and local naming rows.

Finally apply the Real finite-request selector-budget lock,
\autoref{thm:real-regseqrat-finite-request-fusion-selector-budget-lock}, and
the completion-consumer section exactness theorem,
\autoref{thm:real-regseqrat-completion-consumer-section-exactness}. The lock
prevents a terminal budget consumer from replacing the displayed finite
section by a second selector or off-packet tail route, and section exactness
says that completion-facing acceptance is exactly factorization through that
section. Repacking these two Real-side facts through the RegSeqRat
correspondence gives the stated terminal factorization and no additional
exported coordinate.
\end{proof}

\begin{theorem}[RegSeqRat finite-request audit-threshold source lock]
\label{thm:regseqrat-finite-request-audit-threshold-source-lock}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ be a public finite
request to $R$ consumed by a $\RealUp$ seal. Suppose the finite request source
section of \autoref{thm:regseqrat-finite-request-source-section} is the same
section through which the terminal budget factorization of
\autoref{thm:regseqrat-finite-request-terminal-budget-factorization} consumes
$S$.

Then the current Phase $\RealUp$ and Completion audit-threshold read on $S$ is
locked to exactly that finite source section. The read is the objectwise
four-face threshold on
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
over the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
It has no coordinate for quotient streams, selected limits, countable choice,
metric-completeness data, aggregate $\formalstatus$, aggregate bridge rows, or
ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply the terminal budget factorization,
\autoref{thm:regseqrat-finite-request-terminal-budget-factorization}. It says
that every terminal budget consumer of $S$ factors through the displayed finite
request source section, with the $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$ faces carried by the local $\BHist$, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.

Next apply the four-face audit-threshold factorization,
\autoref{thm:regseqrat-four-face-audit-threshold-factorization}. Since the
terminal budget factorization has already fixed the finite source section, the
current Phase $\RealUp$ and Completion threshold read can only be read through
the same four local faces and the same displayed support rows.

The threshold remains objectwise. Use
\autoref{thm:streamname-four-face-audit-clean-threshold-readback} to read the
StreamName-side threshold from the four local face records, and use
\autoref{thm:dyadicratcore-l10-exit-namecert-interface} to keep the
DyadicRatCore, StreamName, RegSeqRat, and Real rows on the shared $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ interface.

Finally invoke \autoref{thm:real-l10-current-phase-exit-audit-pullback}. The
Phase Real and Completion audit is pulled back from the local face records
rather than from a cached route-level status. Therefore quotient streams,
selected limits, countable choice, metric-completeness data, aggregate
$\formalstatus$, aggregate bridge rows, and ambient $\RealUp$ completeness
cannot move the read away from the finite request source section fixed above.
\end{proof}

\begin{theorem}[RegSeqRat finite-request source-section intersection lock]
\label{thm:regseqrat-finite-request-source-section-intersection-lock}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let $S$ and $T$ be public
finite requests to $R$ consumed by local $\RealUp$ seals. Suppose the displayed
source sections of $S$ and $T$ agree on the $\StreamNameUp$ schedule rows, the
$\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance rows, the
$\RegSeqRatUp$ classifier and regularity rows, the componentwise $\hsame$
rows, the displayed $\Cont$ rows, the $\mathsf{Pkg}$ provenance, and the local
$\NameCert_{\RegSeqRatUp}$ rows.

Then the common restriction of the two seal-facing requests is exactly one
finite $\RegSeqRatUp$ source section over those rows. No quotient stream, host
equality, selected limit, choice datum, ambient or metric completeness
principle, or second seal coordinate can distinguish $S$ from $T$ on that
restriction.
\end{theorem}
\begin{proof}
First apply the finite request source section theorem,
\autoref{thm:regseqrat-finite-request-source-section}, to $S$ and to $T$.
The agreement hypotheses identify the displayed schedule, dyadic, classifier,
regularity, transport, continuation, provenance, and local naming rows of the
two finite source packets.

Next pass to the seal-visible side with
\autoref{thm:regseqrat-finite-request-real-seal-correspondence}. The local
$\RealUp$ seals see only the restriction of those finite source packets, so
the same displayed rows give one seal-facing restriction for both requests.

Use the support composition theorem,
\autoref{thm:regseqrat-finite-request-support-face-composition}, to compose
the two agreed support faces through their common displayed rows. The composed
support face still contains exactly the StreamName, DyadicRatCore, RegSeqRat,
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and local $\NameCert_{\RegSeqRatUp}$ rows
named in the statement.

Finally apply the terminal budget factorization theorem,
\autoref{thm:regseqrat-finite-request-terminal-budget-factorization}, to each
seal-facing request. Every terminal consumer factors through the finite source
section already identified above. Since that section carries no quotient
stream, host equality, selected limit, choice datum, completeness principle,
or second seal coordinate, no such external datum can separate the two
requests on the common restriction.
\end{proof}

\begin{theorem}[RegSeqRat finite-request intersection chain stability]
\label{thm:regseqrat-finite-request-intersection-chain-stability}
Let $R$ be an accepted $\RegSeqRatUp$ packet, and let
$S_0,\ldots,S_n$ be a finite nonempty chain of accepted public finite
requests to $R$ consumed by local $\RealUp$ seals. Suppose each adjacent pair
$(S_i,S_{i+1})$ agrees on the displayed $\StreamNameUp$ schedule rows, the
$\DyadicRatCoreUp$ endpoint, radius, and dyadic-distance rows, the
$\RegSeqRatUp$ classifier and regularity rows, the componentwise $\hsame$
rows, the displayed $\Cont$ rows, the $\mathsf{Pkg}$ provenance, and the
local $\NameCert_{\RegSeqRatUp}$ rows. Suppose also that every adjacent pair
agrees on its support subpacket and on the classifier-visible finite request
section over those rows.

Then every pairwise common restriction determined by the chain has the same
Real-seal-facing finite $\RegSeqRatUp$ source section. The direct restriction
from $S_0$ to $S_n$ and every iterated adjacent restriction determine that
same section. The statement does not identify quotient stream equality, host
real equality, selected limits, choice data, ambient or metric completeness,
duplicate $\RealUp$ seal coordinates, aggregate formalstatus rows, or bridge
rows.
\end{theorem}
\begin{proof}
First lock each adjacent intersection. Apply
\autoref{thm:regseqrat-finite-request-source-section-intersection-lock} to
every adjacent pair $(S_i,S_{i+1})$. The hypotheses give exactly the displayed
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and local $\NameCert_{\RegSeqRatUp}$ rows required by that
lock, so each adjacent common restriction has one Real-seal-facing finite
source section.

Next compose the support faces along the chain. Use
\autoref{thm:regseqrat-finite-request-support-face-composition} for each
two-leg composite and then
\autoref{thm:regseqrat-finite-request-support-face-chain-induction} for the
finite nonempty chain. These results identify all parenthesized adjacent
support-face composites with the direct $S_0$ to $S_n$ support face, while
keeping only the displayed StreamName, DyadicRatCore, RegSeqRat, $\hsame$,
$\Cont$, $\mathsf{Pkg}$, and local naming rows.

Finally compare the source sections read from those support faces. The
section-refinement composition theorem,
\autoref{thm:regseqrat-finite-request-section-refinement-composition}, says
that the direct restriction and the iterated adjacent restriction have the
same finite request section and the same local $\RealUp$ seal on the displayed
rows. Substituting the adjacent intersection locks into this comparison gives
one Real-seal-facing finite $\RegSeqRatUp$ source section for every pairwise
common restriction determined by the chain.

The cited lock, support-composition, chain-induction, and
section-refinement routes are all finite BEDC routes over displayed request
rows. None supplies a quotient stream equality, host real equality, selected
limit, choice datum, completeness principle, duplicate Real seal coordinate,
aggregate formalstatus row, or bridge row. Hence the chain stability result
does not claim any of those objects.
\end{proof}
