\begin{theorem}[RegSeqRat StreamName cover-refinement seal handoff]
\label{thm:regseqrat-streamname-cover-refinement-seal-handoff}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over one observation map, and let $P$ be an accepted $\RegSeqRatUp$ packet
whose scheduled reads consume every member of $\mathcal W$. If a finite-window
$\RealUp$ seal handoff is read from the same packet, then that seal-facing
read factors through exactly the public $\StreamNameUp$ finite-window
interface together with the displayed $\mathsf{InBundle}$ rows, pointwise
$\RatUp$ classifier rows, the $\DyadicRatCoreUp$ denominator ledger, $\hsame$,
$\Cont$, and $\mathsf{Pkg}$ provenance exposed by $P$.

Thus the cover-refinement handoff supplies no quotient stream, host real
equality, hidden limit selector, metric-completeness datum, or $\RealUp$
completeness row beyond the finite public window interface and its displayed
regular-rational ledgers.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-cover-refinement-exhaustion}. The finite
cover family over the common observation map is exhausted by public
$\StreamNameUp$ finite-window rows, so every covered read is already visible
through the public window interface and its $\mathsf{InBundle}$ membership
rows.

Next use \autoref{thm:regseqrat-streamname-dyadic-seal-refinement-lock}. For
each covered window consumed by $P$, the public schedule rows lock to the
same pointwise $\RatUp$ classifier rows and to the
$\DyadicRatCoreUp$ denominator ledger carried by the accepted regular-rational
packet.

Now apply \autoref{thm:regseqrat-tail-seal-diagonal-window-coherence}. The
finite cover refinements and the shifted diagonal reads present one coherent
finite $\mathsf{BHist}$ surface, with the same $\hsame$, $\Cont$, and
$\mathsf{Pkg}$ rows wherever the cover windows overlap.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal
consumes only that finite regular-rational source surface, so the handoff
factors through the public $\StreamNameUp$ finite-window interface and cannot
read a quotient stream, host real equality, hidden limit selector, metric
completion, or $\RealUp$ completeness coordinate.
\end{proof}

\begin{theorem}[RegSeqRat tail-stable window cover exhaustion]
\label{thm:regseqrat-tail-stable-window-cover-exhaustion}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over one accepted $\RegSeqRatUp$ packet. If every member of $\mathcal W$ is
stable under shifted-tail regularity closure and the overlaps of
$\mathcal W$ glue by refined-window gluing, then every finite-window
$\RealUp$ seal read over that packet factors through exactly the public
$\StreamNameUp$ windows, the pointwise $\RatUp$ classifier rows, the
$\DyadicRatCoreUp$ denominator and radius ledgers, and the displayed
$\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ provenance.

The factorization exports no quotient stream, host real equality, hidden
limit selector, metric-completeness datum, completion point, or additional
$\RealUp$ seal coordinate beyond the finite tail-stable cover surface.
\end{theorem}
\begin{proof}
Start with the cover-refinement handoff of
\autoref{thm:regseqrat-streamname-cover-refinement-seal-handoff}. It reads the
$\RealUp$ seal only through the public $\StreamNameUp$ finite-window
interface, the displayed $\mathsf{InBundle}$ rows, pointwise $\RatUp$
classifier rows, dyadic denominator ledger, and the stated provenance rows.

Apply \autoref{thm:regseqrat-shifted-tail-regularity-closure} to each window
in the cover. Tail stability keeps the scheduled regularity rows inside the
same accepted $\RegSeqRatUp$ packet after the shifted-tail read, so the seal
cannot leave the finite public cover.

Use \autoref{thm:regseqrat-refined-window-gluing} on every overlap. The
overlap rows glue the public windows into one finite source surface while
preserving the pointwise classifier rows, the dyadic denominator and radius
ledgers, and the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. The $\RealUp$ seal
handoff consumes only the finite regular-rational packet just assembled, so
the tail-stable cover exhausts the whole seal-facing source surface and
leaves no off-table quotient, host-equality, completion, or extra seal row to
read.
\end{proof}

\begin{theorem}[RegSeqRat tail-stable cover common-window lock]
\label{thm:regseqrat-tail-stable-cover-common-window-lock}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over one accepted $\RegSeqRatUp$ packet. Suppose the cover is tail-stable,
every overlap glues by refined-window gluing, and two $\RealUp$ seal
consumers read through members of $\mathcal W$. Then the two seal reads factor
through one accepted common finite window.

The common window exposes exactly the $\StreamNameUp$ schedule rows, the
$\DyadicRatCoreUp$ endpoint and radius ledgers, the $\RegSeqRatUp$
classifier and regularity ledgers, and the displayed $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ provenance. It exposes no quotient stream,
host real equality, selected limit, metric-completeness datum, completion
point, or additional $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:regseqrat-tail-stable-window-cover-exhaustion} to the cover.
Each seal consumer is forced onto the finite tail-stable cover surface, so
neither read can leave the public $\StreamNameUp$ windows and their displayed
regular-rational ledgers.

Next connect the two selected cover members by the finite overlap chain and
apply \autoref{thm:regseqrat-refined-window-chain-exhaustion}. The overlap
gluing hypotheses repack that chain into one accepted common finite window
whose rows are the displayed schedule, endpoint, radius, classifier,
regularity, transport, package, and naming rows.

Use \autoref{thm:regseqrat-common-refinement-classifier-determinacy} on the
overlapping classifier reads. The determinacy row identifies the source rows
seen by the two consumers, so their apparent cover-window origins are two
restrictions of the same accepted common packet.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. Since the seal
handoff consumes exactly that finite regular-rational source surface, both
consumers factor through the single common window and no quotient-stream,
host-equality, selected-limit, completion, metric-completeness, or extra seal
coordinate remains available.
\end{proof}

\begin{theorem}[RegSeqRat finite-cover nerve descent]
\label{thm:regseqrat-finite-cover-nerve-descent}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over an accepted $\RegSeqRatUp$ packet $P$. Suppose every nonempty finite
intersection of members of $\mathcal W$ glues by
\autoref{thm:regseqrat-refined-window-gluing}. Suppose also that the
pairwise tail-stable common-window locks agree on the displayed
$\DyadicRatCoreUp$ endpoint and radius rows, the $\RegSeqRatUp$ classifier
and regularity ledgers, the $\hsame$ and $\Cont$ routes, and the $\Pkg$ and
$\NameCert$ provenance rows carried by $P$. Then all $\RealUp$ seal consumers
over the cover descend to one finite seal-facing source packet.

The descended packet is a public finite $\StreamNameUp$ source surface whose
seal rows are exactly the displayed regular-rational rows named above. It
does not introduce quotient streams, host real equality, selected limits,
metric completeness, completion points, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:regseqrat-streamname-cover-refinement-seal-handoff}. Every
seal-facing read over the cover is already a read from the public
$\StreamNameUp$ windows and the finite regular-rational rows exposed by $P$.

Next use \autoref{thm:regseqrat-tail-stable-window-cover-exhaustion}. The
tail-stable cover surface exhausts the available seal-facing source rows, so
no seal consumer can leave the displayed schedule, classifier, dyadic,
transport, package, or naming data.

For each pair of cover members, apply
\autoref{thm:regseqrat-tail-stable-cover-common-window-lock}. The pairwise
locks identify the common finite-window source rows seen by the two local
seal consumers. The stated agreement on endpoint, radius, classifier,
regularity, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows makes these
pairwise packets compatible along every nonempty finite intersection.

Now order the finite nerve by any enumeration of its nonempty intersections
and apply \autoref{thm:regseqrat-refined-window-chain-exhaustion}. The
intersection gluing hypotheses repack the compatible pairwise common windows
into one accepted finite source packet for the whole cover.

Finally invoke \autoref{thm:regseqrat-real-seal-handoff}. Since the terminal
$\RealUp$ seal consumes only the accepted finite regular-rational packet, all
cover-local seal consumers descend through that single seal-facing source
packet, with no quotient-stream, host-equality, selected-limit, completion,
metric-completeness, or ambient-completeness coordinate available.
\end{proof}

\begin{theorem}[RegSeqRat finite-cover nerve induction]
\label{thm:regseqrat-finite-cover-nerve-induction}
Let $\mathcal W$ be a finite cover family of public $\StreamNameUp$ windows
over an accepted $\RegSeqRatUp$ packet $P$. Suppose every nonempty finite
intersection of members of $\mathcal W$ glues by
\autoref{thm:regseqrat-refined-window-gluing}, and suppose each lower
dimensional face satisfies the pairwise common-window lock of
\autoref{thm:regseqrat-tail-stable-cover-common-window-lock}. Then induction
over the finite nerve of $\mathcal W$ produces one global seal-facing source
packet.

The global packet preserves exactly the displayed $\DyadicRatCoreUp$ endpoint
and radius rows, the $\RegSeqRatUp$ classifier and regularity ledgers, the
$\hsame$ and $\Cont$ routes, and the $\Pkg$ and $\NameCert$ provenance rows
carried by $P$.

It introduces no quotient stream, host real equality, selected limit,
metric-completeness datum, completion point, or ambient $\RealUp$
completeness row.
\end{theorem}
\begin{proof}
For the base case, take a singleton nonempty intersection in the nerve and
apply \autoref{thm:regseqrat-streamname-cover-refinement-seal-handoff}. The
single local seal read is already a public $\StreamNameUp$ finite-window read
from the displayed regular-rational rows of $P$.

For the induction step, adjoin one nonempty intersection to a nerve segment
whose seal-facing packet has already been assembled. Apply
\autoref{thm:regseqrat-tail-stable-window-cover-exhaustion} to keep the new
intersection inside the tail-stable public cover surface.

On each overlap between the new intersection and the assembled segment, use
\autoref{thm:regseqrat-tail-stable-cover-common-window-lock}. The lower
dimensional face hypotheses identify the same endpoint, radius, classifier,
regularity, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows on the common
finite window.

Now apply \autoref{thm:regseqrat-refined-window-chain-exhaustion}. The refined
overlap chain repacks the previously assembled packet and the new intersection
packet into one accepted finite source packet with the same displayed rows.

Finally invoke \autoref{thm:regseqrat-finite-cover-nerve-descent}. The descent
theorem identifies the terminal global seal-facing source for the whole finite
cover, and the construction leaves no quotient stream, host real equality,
selected limit, metric completion, completion point, or ambient $\RealUp$
completeness coordinate to read.
\end{proof}
