\begin{theorem}[RegSeqRat seal-route visible source normal form]\label{thm:regseqrat-seal-route-visible-source-normal-form}
Every accepted $\RealUp$ seal route consumed from an accepted $\RegSeqRatUp$
packet factors through one visible finite source surface. That surface consists
exactly of the displayed $\StreamNameUp$ schedule rows, the
$\DyadicRatCoreUp$ endpoint, radius, and distance ledgers, the $\RegSeqRatUp$
regularity rows and transported classifier rows, the finite $\mathsf{BHist}$
packet rows, the displayed $\hsame$ transports, the visible $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and the local $\NameCert_{\RegSeqRatUp}$ rows.

Conversely, any finite route package carrying exactly those rows replays to
the same terminal finite $\RealUp$ seal route. The normal form has no
coordinate for quotient stream equality, host real equality, a selected limit,
a metric-completion point, $\RealUp$ completeness, or standard-bridge data.
\end{theorem}
\begin{proof}
Begin with the accepted seal route and apply
\autoref{thm:regseqrat-real-seal-route-exclusion-package}. The route can read
only the displayed schedule, dyadic, regularity, transport, continuation,
package, and local naming rows, and it has no channel for the excluded
real-number or bridge coordinates.

Next apply \autoref{thm:regseqrat-cover-normal-form-real-seal}. The exposed
rows are repacked as one canonical finite $\mathsf{BHist}$ packet carrying the
$\StreamNameUp$ windows, $\DyadicRatCoreUp$ endpoint, radius, and distance
ledgers, regularity and classifier rows, $\hsame$, $\Cont$, $\mathsf{Pkg}$,
and $\NameCert$ provenance.

Use \autoref{thm:regseqrat-real-seal-classifier-exhaustion} inside that packet.
It identifies the classifier component with the transported $\RegSeqRatUp$
classifier surface and shows that no quotient stream, host equality,
completion point, selected limit, or $\RealUp$ completeness row remains to be
read.

Finally invoke \autoref{thm:regseqrat-real-seal-schedule-confluence}. Any two
accepted seal routes exposing the same displayed rows replay through one
terminal finite $\RealUp$ seal route. Thus the common finite packet is the
unique visible source surface consumed by the $\RealUp$ seal handoff, and every
accepted route factors through precisely that surface.
\end{proof}
