\begin{theorem}[RegSeqRat Real seal support-removal obstruction]
\label{thm:regseqrat-real-seal-support-removal-obstruction}
Let $P$ be an accepted public $\RegSeqRatUp$ read whose public exit is a
$\RealUp$ seal through the L10 route displayed by
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness}. Remove from
that route any one of the four displayed faces
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
or remove any displayed support row among the $\BHist$ route rows,
componentwise $\hsame$ rows, $\Cont$ rows, $\mathsf{Pkg}$ provenance rows, or
local $\NameCert$ rows. Then the remaining data do not form a valid public
$\RealUp$ seal route for $P$.

No quotient stream, host real equality, selected limit, ambient or
metric-completeness datum, choice datum, aggregate $\formalstatus$ row,
aggregate bridge row, or second $\RealUp$ seal coordinate compensates for the
missing face or support row.
\end{theorem}
\begin{proof}
First remove one displayed face. By
\autoref{thm:regseqrat-streamname-dyadic-real-four-stage-consumer-minimality},
every valid public seal consumer for the accepted read passes through the
StreamName schedule face, the DyadicRatCore endpoint and radius face, the
RegSeqRat classifier and regularity face, and the Real seal face. Omitting any
one of these four surfaces therefore places the attempted consumer outside the
displayed public route.

Next remove a displayed support row. Apply
\autoref{thm:regseqrat-streamname-dyadic-real-handoff-exactness} to identify
the route as one finite BEDC handoff, with the visible $\BHist$ rows,
componentwise $\hsame$ rows, $\Cont$ rows, $\mathsf{Pkg}$ provenance rows, and
local $\NameCert$ rows carrying the same accepted read from source schedules to
the terminal seal. Without one of those support rows, the four faces no longer
sit in a single certified handoff route for $P$.

It remains to rule out replacement data. The finite-cover results
\autoref{thm:regseqrat-real-seal-finite-cover-gluing},
\autoref{thm:regseqrat-real-seal-finite-cover-induction-step}, and
\autoref{thm:regseqrat-real-seal-finite-cover-associativity} keep all glued
and regrouped public seal packets inside the same four displayed faces and
the same $\BHist$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ support
rows. Their exclusion clauses leave no coordinate for quotient streams, host
real equality, selected limits, ambient or metric completeness, choice data,
aggregate $\formalstatus$ rows, aggregate bridge rows, or second seal
coordinates. Thus none of these objects can repair the missing displayed face
or support row, and no valid public $\RealUp$ seal route remains.
\end{proof}
