\begin{theorem}[RegSeqRat tail-budget exhaustion]
\label{thm:regseqrat-tail-budget-exhaustion}
Every finite dyadic request admitted by the $\RegSeqRatUp$ tail selector is exhausted by a displayed tail budget and cannot escape the $\RealUp$ seal route. The displayed budget contains the StreamName window row, DyadicRatCore tolerance row, RegSeqRat regularity row, selected tail row, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Thus no admitted finite dyadic request can be consumed as a Real-facing request without passing through the same tail-budget packet and the same public seal boundary.
\end{theorem}
\begin{proof}
Begin with the tail-budget handoff of \autoref{thm:regseqrat-tail-budget-meet-handoff}. It names the finite StreamName window, DyadicRatCore observation rows, RegSeqRat regularity rows, and local support rows that any Real-facing tail-budget request must display.

Apply the tail selector Real-seal exhaustion theorem, \autoref{thm:regseqrat-tail-budget-terminal-real-seal}. The selector cannot export a finite dyadic request to the Real seal unless the displayed budget rows already carry that request.

Now use the non-escape result \autoref{thm:regseqrat-tail-budget-nonescape}. It removes quotient sequence equality, selected limits, countable choice, and ambient completeness from the tail-budget consumer route.

The remaining data are exactly the displayed tail budget and the public RealUp seal route. Therefore every admitted finite dyadic request is exhausted by that budget and cannot escape the seal boundary.
\end{proof}

\begin{theorem}[RegSeqRat tail-budget exit status product]
\label{thm:regseqrat-tail-budget-exit-status-product}
Every accepted finite dyadic request admitted by the $\RegSeqRatUp$ tail selector and consumed as a Phase Real and Completion endpoint is audit-readable only as the componentwise status product of four local face records: the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, and the $\RealUp$ seal row. Each face contributes its own $\mathsf{closurestatus}$ and $\mathsf{formalstatus}$ record, while the shared transport is only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

The exit read contains no quotient stream, host equality, selected limit, countable-choice principle, ambient completeness datum, metric-completion datum, bridge row, aggregate $\mathsf{formalstatus}$ token, or promotion from one status axis to the other.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regseqrat-tail-budget-exhaustion}. It puts every admitted finite dyadic request on the displayed tail-budget packet and keeps the Real-facing consumer inside the same public $\RealUp$ seal boundary.

Next apply \autoref{thm:regseqrat-four-face-terminal-pullback} and \autoref{thm:regseqrat-dyadic-tail-real-seal-status-exhaustion}. These results identify the terminal read as the four-face ledger consisting of the DyadicRatCore tolerance face, StreamName finite-window face, RegSeqRat regularity and classifier face, and terminal Real seal face, transported only by the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Finally read the ledger through the two-axis discipline of \autoref{ch:closure-and-verification-discipline}. A face's closure record and verification record remain local to that face, so their product is only a componentwise audit surface. It cannot add a quotient stream, host equality, selected limit, countable-choice principle, completeness datum, bridge row, aggregate verification token, or implication from one axis to the other.
\end{proof}

\begin{theorem}[RegSeqRat tail-budget status product reverse]
\label{thm:regseqrat-tail-budget-status-product-reverse}
Any finite $\RegSeqRatUp$ tail-budget packet exposing exactly the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, the local $\RealUp$ seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows presents the same public Phase Real and Completion exit status product.

The packet has no aggregate $\mathsf{formalstatus}$ coordinate, bridge coordinate, route-level completeness coordinate, quotient stream, host real equality, selected limit, or countable-choice selector. Its public read is therefore exactly the componentwise four-face status product of \autoref{thm:regseqrat-tail-budget-exit-status-product}.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-tail-budget-exhaustion}. Every admitted finite dyadic request has already been forced onto the displayed tail-budget packet before the public $\RealUp$ seal can consume it.

Next use \autoref{thm:regseqrat-four-face-terminal-pullback}. The exposed DyadicRatCore tolerance ledger, StreamName finite-window row, RegSeqRat regularity and classifier row, and local Real seal row form the same terminal four-face pullback over the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Now apply \autoref{thm:regseqrat-tail-budget-nonescape}. No quotient stream, host equality, selected limit, countable-choice principle, ambient completeness datum, or metric-completion datum can enter the consumer route from outside those rows.

Finally use \autoref{thm:regseqrat-tail-budget-support-minimality}. Since the displayed face rows and support rows are exactly the support-minimal packet, adding a route-level $\mathsf{formalstatus}$ token, bridge row, or completeness coordinate would not be a component of the accepted public read.

Read the result through the two-axis discipline of \autoref{ch:closure-and-verification-discipline}. The same face-local rows reconstruct the same componentwise status product, and no route-level token is introduced.
\end{proof}

\begin{theorem}[RegSeqRat four-face exit consumer normal form]
\label{thm:regseqrat-four-face-exit-consumer-normal-form}
Every Phase Real and Completion consumer that reads an accepted finite dyadic request from the $\RegSeqRatUp$ selector factors through exactly four displayed faces: the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, and the $\RealUp$ seal row. The transport between these faces is only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Conversely, any consumer exposing these four faces with the same displayed transport has the same public L10 exit read. The normal form exports no quotient stream, host real equality, selected limit, countable-choice selector, metric-completeness datum, aggregate $\mathsf{formalstatus}$ row, or bridge row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regseqrat-tail-budget-exit-status-product}. It places every accepted finite dyadic request consumed at a Phase Real and Completion endpoint on the four componentwise status faces and records the admissible transport rows.

Next apply \autoref{thm:regseqrat-four-face-terminal-pullback}. The terminal pullback identifies the same four faces as a single finite $\BHist$ surface and shows that the route is carried only by the displayed $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Use \autoref{thm:streamname-four-object-exit-exactness} and \autoref{thm:dyadicratcore-phase-real-completion-objectwise-exit-equivalence} to align the consumer-side finite-window read with the objectwise DyadicRatCore, StreamName, RegSeqRat, and Real exit records. These identifications make the forward factorization and the reverse same-read criterion the same public L10 read.

Finally apply the two-axis discipline of \autoref{sec:roadmap-closure-and-verification-axes}. It keeps closure rows, verification rows, and bridge rows local to their own faces, so the consumer normal form cannot introduce quotient streams, host real equality, selected limits, countable choice, metric-completeness data, aggregate $\mathsf{formalstatus}$ rows, or bridge rows.
\end{proof}

\begin{theorem}[RegSeqRat tail-budget finite-window refusal localization]
\label{thm:regseqrat-tail-budget-finite-window-refusal-localization}
Let a finite dyadic request be addressed to a $\RegSeqRatUp$ tail-budget route. If the request is not accepted as a Phase Real and Completion four-face exit consumer, then the defect is localized to at least one displayed face row or one displayed support row.

The possible face rows are exactly the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, and the $\RealUp$ seal row. The possible support rows are exactly $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Quotient stream equality, host real equality, selected limits, countable choice, metric-completeness data, aggregate $\mathsf{formalstatus}$ tokens, aggregate bridge rows, and $\RealUp$ completeness cannot serve as the defect carrier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-tail-budget-exhaustion}. Any finite dyadic request that reaches the tail selector is exhausted by the displayed tail budget before the public $\RealUp$ seal can read it, so a non-accepted request cannot be explained by an off-budget object.

Next use \autoref{thm:regseqrat-tail-budget-exit-status-product}. The accepted endpoint is a componentwise status product over the four listed faces, transported only by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Hence a missing acceptance witness must remove one of those component rows or one of those transport rows.

Now apply \autoref{thm:regseqrat-four-face-exit-consumer-normal-form}. That normal form is also the reverse public-read criterion: exposing the same four faces with the same displayed transport gives the same L10 exit read. Therefore any request that does not expose such a read has its defect on the named face or support rows.

Finally read the conclusion through the two-axis discipline of \autoref{sec:roadmap-closure-and-verification-axes}. Since closure rows, verification rows, and bridge rows do not promote into one another, no quotient equality, host equality, selected limit, choice principle, completeness datum, aggregate status token, aggregate bridge row, or $\RealUp$ completeness claim can replace the missing displayed row.
\end{proof}

\begin{theorem}[RegSeqRat tail-budget support minimality]
\label{thm:regseqrat-tail-budget-support-minimality}
Every accepted finite dyadic request consumed by the Phase Real and Completion $\RegSeqRatUp$ tail-budget route has a support-minimal four-face packet. Its face rows are exactly the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, and the $\RealUp$ seal row. Its shared support rows are exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Deleting any one of these face or support rows destroys the accepted public read. Quotient stream equality, host real equality, selected limits, countable choice, metric-completeness data, aggregate $\mathsf{formalstatus}$ tokens, aggregate bridge rows, and $\RealUp$ completeness cannot replace the missing row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regseqrat-four-face-exit-consumer-normal-form}. The forward direction factors every accepted finite dyadic request through the four displayed faces and the listed transport support. The reverse direction says that the same four faces with the same support rows give the same public L10 exit read.

Now delete one displayed face row or one displayed support row. The resulting packet no longer satisfies the reverse same-read criterion, so it is not an accepted four-face exit consumer for the same request.

Apply \autoref{thm:regseqrat-tail-budget-finite-window-refusal-localization} to the failed read. Its defect must localize to one of the displayed face rows or support rows, and the localization list is exactly the list removed from the packet above.

Finally use \autoref{thm:regseqrat-tail-budget-exit-status-product} together with the two-axis discipline of \autoref{sec:roadmap-closure-and-verification-axes}. Aggregate verification tokens and bridge rows are not component rows of the status product, and neither quotient equality, host equality, selected limits, choice principles, completeness data, nor $\RealUp$ completeness can promote into the missing face or support row. Thus no displayed row can be dropped.
\end{proof}

\begin{theorem}[RegSeqRat tail-window stability]
\label{thm:regseqrat-tail-window-stability}
Let an accepted $\RegSeqRatUp$ tail-budget packet expose a finite tail window as a Phase Real and Completion four-face exit consumer. If that finite tail window is replaced by a certified finer tail window with the same displayed request and support rows, then the public exit read preserves the $\DyadicRatCoreUp$ tolerance ledger, the $\StreamNameUp$ window row, the $\RegSeqRatUp$ classifier row, and the $\RealUp$ seal row.

The stability read exports no quotient stream equality, selected limit, countable-choice selector, $\RealUp$ completeness datum, metric-completion datum, aggregate $\mathsf{formalstatus}$ token, or bridge row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regseqrat-tail-budget-exhaustion}. The original accepted request is already exhausted by the displayed tail budget before the public $\RealUp$ seal can consume it.

Apply \autoref{thm:regseqrat-tail-budget-exit-status-product}. The public read is componentwise: the DyadicRatCore tolerance ledger, StreamName finite-window row, RegSeqRat regularity and classifier row, and Real seal row remain separate faces over the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Now use \autoref{thm:regseqrat-four-face-exit-consumer-normal-form}. A certified finer tail window with the same displayed support rows exposes the same four-face consumer normal form, so it has the same L10 public exit read as the original window.

Finally apply \autoref{thm:regseqrat-tail-budget-support-minimality}. Since the four face rows and shared support rows are exactly the support-minimal packet, the refinement can neither drop a displayed row nor replace one by quotient stream equality, a selected limit, countable choice, $\RealUp$ completeness, metric completeness, an aggregate status token, or a bridge row.
\end{proof}

\begin{theorem}[RegSeqRat tail-budget common-threshold exhaustion]
\label{thm:regseqrat-tail-budget-common-threshold-exhaustion}
Let $q_{0}$ and $q_{1}$ be accepted finite dyadic requests for the $\RegSeqRatUp$ tail-budget route. Suppose they share the same displayed $\StreamNameUp$ schedule row, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ classifier and regularity rows, local $\RealUp$ seal row, and displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Then the two requests admit one common displayed threshold packet. Every Real-facing consumer of either request factors through that packet and the same four-face exit surface. The common-threshold read exports no quotient stream, selected limit, host equality, countable choice, metric-completion datum, aggregate $\mathsf{formalstatus}$ token, or bridge row capable of distinguishing the two requests.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regseqrat-tail-window-stability}. Since the requests share the same schedule, tolerance, classifier, regularity, Real-seal, and support rows, refining either finite tail window along the common support preserves the same four displayed faces.

Next apply \autoref{thm:regseqrat-four-face-exit-consumer-normal-form}. A Real-facing consumer can read an accepted request only through the DyadicRatCore tolerance face, StreamName finite-window face, RegSeqRat classifier face, Real seal face, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Use \autoref{thm:regseqrat-tail-budget-support-minimality}. The shared face and support rows are exactly the support-minimal packet, so a common displayed threshold can be chosen inside that finite support and no omitted row can be recovered from outside it.

Finally the normal-form non-escape clauses remove quotient streams, selected limits, host equality, countable choice, metric-completion data, aggregate verification tokens, and bridge rows from the consumer route. Thus no Real-facing consumer distinguishes $q_{0}$ from $q_{1}$ except through the common displayed threshold packet, and both requests factor through it.
\end{proof}
