\section{RegSeqRat Terminal Four-Face Axis Separation}
\label{sec:regseqrat-terminal-four-face-axis-separation}

\begin{theorem}[RegSeqRat terminal four-face axis separation]
\label{thm:regseqrat-terminal-four-face-axis-separation}
Every $\RegSeqRatUp$ terminal four-face read through
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp
$$
supplies only the paper-side finite boundary whose support rows are
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
The read cannot raise a formal-status token for any of the four faces, create
a standard bridge row, assert ambient $\RealUp$ completeness, introduce
quotient stream equality, or supply metric-completeness data.

Thus downstream Phase Real and Completion consumers may use the terminal
four-face packet only as a finite manuscript boundary. Verification status,
bridge status, quotient identification, and completeness data must still be
read from the relevant face's own closurestatus, Lean target, and bridge
boundary.
\end{theorem}
\begin{proof}
Start with \autoref{thm:regseqrat-terminal-four-face-correspondence}. It
identifies terminal RegSeqRat agreement exactly with the visible four-face
inventory and transports that agreement only through the displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Next apply \autoref{thm:regseqrat-four-face-hub-sibling-route}. The route is
not an isolated RegSeqRat coordinate: it passes through the DyadicRatCore,
StreamName, and Real sibling chapters before it is consumed as a Real-facing
handoff, while retaining the same finite support rows.

Now invoke \autoref{thm:streamname-real-completion-four-object-exit-route}.
It reads the Phase Real and Completion exit packet as exactly the four faces
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, with no
quotient stream equality, host sequence equality, selected limit, ambient
$\RealUp$ completeness theorem, metric-completeness datum, countable-choice
row, or standard bridge row.

Finally use \autoref{thm:real-regseq-streamname-cauchy-completion-interface}.
The Real-facing completion interface consumes the same finite window,
regular-rational readback, dyadic observation ledger, seal row, componentwise
$\hsame$ transport, displayed $\Cont$ route, package provenance, and local
$\NameCert$ row. Since the cited routes contain no verification-axis token,
standard bridge row, ambient completeness principle, quotient stream
equality, or metric-completeness coordinate, the terminal four-face read
separates the paper-side boundary from those independent axes.
\end{proof}

\begin{theorem}[RegSeqRat terminal four-face status pullback]
\label{thm:regseqrat-terminal-four-face-status-pullback}
An accepted $\RegSeqRatUp$ terminal four-face read satisfies the current Phase Real and Completion objectwise status boundary if and only if it exposes the four local face records for
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
where each face is read from its own $\mathsf{closurestatus}$, $\mathsf{formalstatus}$, $\mathsf{leantarget}$, and $\mathsf{bridgestatus}$ rows, together with the shared support
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

The pullback contains no aggregate $\mathsf{formalstatus}$ row, aggregate bridge token, selected limit, quotient stream equality, metric-completeness datum, countable-choice row, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
For necessity, begin with \autoref{thm:regseqrat-terminal-four-face-axis-separation}. It separates the terminal four-face paper boundary from verification status, bridge status, quotient identification, selected limits, metric-completeness data, countable choice, and ambient real completeness.

Next apply \autoref{thm:regseqrat-terminal-four-face-correspondence}. The accepted RegSeqRat terminal read has exactly the visible four-face inventory, and the $\RegSeqRatUp$ classifier and readback rows are one of those local faces rather than an aggregate route token.

Now use \autoref{thm:streamname-real-completion-four-object-exit-route}. The current Phase Real and Completion route consumes precisely the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

For sufficiency, start with the four local face records and the shared support rows. Apply \autoref{thm:dyadicratcore-l10-face-status-pullback} to read the local $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ status rows from their own closurestatus, formalstatus, leantarget, and bridgestatus entries.

Finally invoke \autoref{thm:real-l10-objectwise-face-status-exit}. The Real-side criterion consumes exactly those objectwise face records together with the displayed finite support, so the accepted RegSeqRat terminal read satisfies the current Phase Real and Completion objectwise status boundary.

The exclusions follow from the same citations. The axis-separation theorem and the dyadic pullback theorem expose no aggregate formalstatus, aggregate bridge, selected limit, quotient stream equality, metric-completeness datum, countable-choice row, or ambient $\RealUp$ completeness coordinate, and the four-object route plus the Real objectwise criterion provide no further row in which such data could be stored.
\end{proof}
