\newcommand{\CategoryHomCarrierEOneTargetMorphismDescentProof}{%
Unpack the hom-carrier fields. The source unary witness is unchanged. Unary
inversion removes the visible constructor from both the target carrier and the
morphism carrier, and the right step-rule inversion for $\ContR$ removes the
same visible constructor from the continuation ledger. Repacking these fields
gives $\mathsf{CategoryHomCarrier}(a,r,k)$.}

\newcommand{\CategoryHomCarrierEOneTargetMorphismExactnessIffProof}{%
The forward implication is the one-headed target and morphism descent theorem.
Conversely, a tail hom-carrier supplies the unary source, unary morphism tail,
and tail continuation $\ContR(a,k,r)$. The one-headed morphism target
exactness theorem repacks these data as the displayed one-headed target and
morphism hom-carrier.}

\newcommand{\CategoryHomCarrierEOneSourceMorphismTargetExactnessProof}{%
Unpack the hom-carrier witness. The continuation field forces the target to
have a visible one constructor; removing that constructor gives
\(\ContR(\Eone(a),k,r)\). The source, morphism, and target unary witnesses
invert through the same visible constructors. Conversely, the displayed target
equation, the three unary witnesses, and the one-step continuation rule rebuild
the hom-carrier fields.}

\newcommand{\CategoryHomCarrierEOneEndpointMorphismPayloadDeterminacyProof}{%
Lift the source and target endpoint equalities through the one-headed
constructor. Endpoint-sensitive morphism determinacy gives
$\hsame(\Eone(k),\Eone(k'))$ for the displayed morphisms. One-headed
constructor inversion removes the visible tag and yields $\hsame(k,k')$.}
