\begin{definition}[Complete global fiber $3+1$ tile]
\label{def:philosophy-complete-global-fiber-three-one-tile}
Let $E:Q_{6}\to C$ be a translation classifier. An axis-aligned
$Q_{2}$ face $F$ is a complete global fiber $3+1$ tile when there are
classes $a,b\in C$ such that
$$
  F=E^{-1}(a)\sqcup E^{-1}(b),
  \qquad
  |E^{-1}(a)|=3,
  \qquad
  |E^{-1}(b)|=1.
$$
Thus the local three-point side is not merely a local multiplicity:
it is the whole global tripleton fiber. Likewise the singleton corner is
the whole global singleton fiber.
\end{definition}

\begin{theorem}[Complete global fiber tiles in the standard code]
\label{thm:philosophy-complete-global-fiber-tiles-standard-code}
Under the two-axis readback and the standard translation classifier, the
complete global fiber $3+1$ tiles are exactly
$$
\begin{array}{c|c|c|c}
  \text{face} & \text{global tripleton} & \text{global singleton}
    & \text{singleton corner}\\
\hline
  \{\mathrm{AUU},\mathrm{AUC},\mathrm{AUA},\mathrm{AUG}\}
    & \mathrm{Ile} & \mathrm{Met} & 11\\
  \{\mathrm{UAA},\mathrm{UAG},\mathrm{UGA},\mathrm{UGG}\}
    & \mathrm{Stop} & \mathrm{Trp} & 11.
\end{array}
$$
\end{theorem}
\begin{proof}
By \autoref{cor:philosophy-standard-code-degeneracy-spectrum}, the only
global tripleton classes of the standard classifier are $\mathrm{Ile}$
and $\mathrm{Stop}$, and the only global singleton classes are
$\mathrm{Met}$ and $\mathrm{Trp}$. The exhaustive local $Q_{2}$
enumeration of \autoref{thm:philosophy-standard-code-axis-aligned-three-one-face-enumeration}
has four $3+1$ faces. The two Phe/Leu faces are excluded because
$\mathrm{Phe}$ is a global doubleton and $\mathrm{Leu}$ is a global
sextupleton. The remaining two faces are the displayed Ile/Met and
Stop/Trp faces, and both have singleton corner $11$.
\end{proof}

\begin{corollary}[Global fibers select the dual control tiles]
\label{cor:philosophy-global-fibers-select-dual-control-tiles}
The pair $\mathrm{Ile}/\mathrm{Met}$ and $\mathrm{Stop}/\mathrm{Trp}$ is
not selected by choosing two examples from the four local $3+1$ faces.
It is selected by imposing the global-fiber condition on the local
$Q_{2}$ spectrum.
\end{corollary}
\begin{proof}
The global-fiber condition eliminates the Phe/Leu local slices and keeps
exactly the two rows of
\autoref{thm:philosophy-complete-global-fiber-tiles-standard-code}.
\end{proof}

\begin{theorem}[Standard-code $Q_{1}$ edge spectrum]
\label{thm:philosophy-standard-code-q-one-edge-spectrum}
The standard translation classifier has $50$ same-class Hamming edges
and $142$ cross-class Hamming edges in $Q_{6}$. By bit direction
$$(b_{1}^{s},b_{1}^{f},b_{2}^{s},b_{2}^{f},b_{3}^{s},b_{3}^{f}),$$
the same-class edge counts are
$$
\begin{array}{c|rrrrrr}
  \text{direction}
    & b_{1}^{s} & b_{1}^{f} & b_{2}^{s}
    & b_{2}^{f} & b_{3}^{s} & b_{3}^{f}\\
\hline
  \text{same-class edges}
    & 0 & 2 & 0 & 1 & 17 & 30\\
  \text{cross-class edges}
    & 32 & 30 & 32 & 31 & 15 & 2.
\end{array}
$$
\end{theorem}
\begin{proof}
For each of the six bit directions, enumerate the $32$ Hamming edges
$x\leftrightarrow x\oplus e_i$. Decode both endpoints to codons and
compare their standard translation labels. The displayed table is the
finite count over the resulting $6\cdot 32=192$ edges.
\end{proof}

\begin{corollary}[Third-position softness]
\label{cor:philosophy-third-position-softness}
The third-position family bit $b_{3}^{f}$ is the most stable Hamming
direction in the standard classifier, with $30$ same-class edges out of
$32$. The first and second shape bits have no same-class edge.
\end{corollary}
\begin{proof}
Read the direction counts in
\autoref{thm:philosophy-standard-code-q-one-edge-spectrum}.
\end{proof}

\begin{theorem}[Same-histogram random edge baseline]
\label{thm:philosophy-same-histogram-random-edge-baseline}
Keep only the standard-code degeneracy histogram
$$
  1:2,\qquad 2:9,\qquad 3:2,\qquad 4:5,\qquad 6:3,
$$
and randomly assign the resulting fibers to the $64$ codons. For a
random unordered pair of distinct codons, the same-class probability is
$$
  p_{\mathrm{same}}
  =
  \frac{\sum_{a}\binom{d_{a}}{2}}{\binom{64}{2}}
  =
  \frac{5}{112}.
$$
Thus the expected number of same-class Hamming edges among the $192$
edges of $Q_{6}$ is
$$
  192\,p_{\mathrm{same}}
  =
  \frac{60}{7}
  \approx 8.57.
$$
The observed standard-code value is $50$, namely
$$
  \frac{50}{60/7}=\frac{35}{6}\approx5.83
$$
times the same-histogram random expectation.
The exact variance of the same-edge count under this same-histogram
model is
$$
  \frac{686964}{92659}\approx7.41,
$$
so the standard deviation is about $2.72$ and the observed value has
z-score about $15.2$.
\end{theorem}
\begin{proof}
The standard degeneracy histogram gives
$$
  \sum_{a}\binom{d_{a}}{2}
  =
  2\binom{1}{2}
  +9\binom{2}{2}
  +2\binom{3}{2}
  +5\binom{4}{2}
  +3\binom{6}{2}
  =
  90.
$$
Since $\binom{64}{2}=2016$, the probability is
$90/2016=5/112$. Multiplying by the $192$ Hamming edges gives $60/7$.
The observed count $50$ is
\autoref{thm:philosophy-standard-code-q-one-edge-spectrum}.
For the variance, separate unordered pairs of Hamming edges into
adjacent edge-pairs, of which there are $64\binom{6}{2}=960$, and
disjoint edge-pairs, of which there are
$\binom{192}{2}-960=17376$. Evaluating the two corresponding
same-fiber probabilities from the fixed fiber sizes gives the displayed
finite variance.
\end{proof}

\begin{corollary}[Local edge smoothness is not a histogram artifact]
\label{cor:philosophy-local-edge-smoothness-not-histogram-artifact}
The standard classifier is not merely a code table with the listed
global degeneracy histogram. It is locally smooth on the Hamming graph:
same-class adjacency is about $5.83$ times the same-histogram random
expectation, and the smoothness is concentrated in the third-base
directions.
\end{corollary}
\begin{proof}
The excess over the histogram baseline is
\autoref{thm:philosophy-same-histogram-random-edge-baseline}. The
directional concentration is
\autoref{cor:philosophy-third-position-softness}.
\end{proof}

\begin{theorem}[Single-nucleotide substitution edge spectrum]
\label{thm:philosophy-single-nucleotide-substitution-edge-spectrum}
If edges are taken to be ordinary one-base substitutions rather than
one-bit flips, then there are $288$ unordered edges. The standard
classifier has the following position-wise spectrum:
$$
\begin{array}{c|rrr|r}
  \text{codon position} & 1 & 2 & 3 & \text{total}\\
\hline
  \text{same-class substitution edges} & 4 & 1 & 64 & 69\\
  \text{cross-class substitution edges} & 92 & 95 & 32 & 219.
\end{array}
$$
\end{theorem}
\begin{proof}
For each codon position, fix the other two bases in $4^{2}$ ways and
connect the four choices at the chosen position by the complete graph
on four bases. This gives $16\binom{4}{2}=96$ edges per position and
$288$ total edges. Decoding both endpoints and comparing their standard
translation labels gives the displayed finite spectrum.
\end{proof}

\begin{corollary}[Two-axis stability matches nucleotide substitution]
\label{cor:philosophy-two-axis-stability-matches-nucleotide-substitution}
The two-axis $Q_{6}$ edge spectrum is not only a formal bit-cube
phenomenon. Ordinary one-base substitution edges show the same
asymmetry: the third codon position has $64$ same-class edges out of
$96$, while the first two positions have only $4$ and $1$.
\end{corollary}
\begin{proof}
Compare \autoref{thm:philosophy-standard-code-q-one-edge-spectrum} with
\autoref{thm:philosophy-single-nucleotide-substitution-edge-spectrum}.
\end{proof}

\begin{theorem}[Standard-code $Q_{2}$ face spectrum]
\label{thm:philosophy-standard-code-q-two-face-spectrum}
The $240$ axis-aligned $Q_{2}$ faces of the standard classifier have
the following multiplicity spectrum:
$$
\begin{array}{c|rrrrr}
  \text{local pattern}
    & 4 & 3+1 & 2+2 & 2+1+1 & 1+1+1+1\\
\hline
  \text{face count}
    & 9 & 4 & 83 & 44 & 100.
\end{array}
$$
By geometric type, the same spectrum refines to
$$
\begin{array}{c|rrrrr|r}
  \text{face type}
    & 4 & 3+1 & 2+2 & 2+1+1 & 1+1+1+1 & \text{total}\\
\hline
  \text{same base}
    & 8 & 1 & 6 & 6 & 27 & 48\\
  \text{cross-base same axis}
    & 1 & 1 & 39 & 18 & 37 & 96\\
  \text{cross-base mixed axis}
    & 0 & 2 & 38 & 20 & 36 & 96.
\end{array}
$$
\end{theorem}
\begin{proof}
The first table is the exhaustive face enumeration already used in
\autoref{thm:philosophy-standard-code-axis-aligned-three-one-face-enumeration},
with all multiplicity patterns retained rather than only the $3+1$
rows. The second table partitions the same faces by whether the two
free bits lie in the same base, in different bases along the same
axis, or in different bases along different axes.
\end{proof}

\begin{theorem}[Standard-code $Q_{3}$ cube spectrum]
\label{thm:philosophy-standard-code-q-three-cube-spectrum}
The $160$ axis-aligned $Q_{3}$ cubes of the standard classifier have
the following multiplicity spectrum:
$$
\begin{array}{c|r}
  \text{local pattern} & \text{cube count}\\
\hline
  2+2+2+2 & 46\\
  1+1+1+1+1+1+1+1 & 21\\
  2+1+1+1+1+1+1 & 21\\
  2+2+2+1+1 & 18\\
  2+2+1+1+1+1 & 11\\
  4+2+2 & 10\\
  4+4 & 10\\
  3+2+2+1 & 9\\
  3+2+1+1+1 & 5\\
  4+2+1+1 & 4\\
  3+1+1+1+1+1 & 2\\
  4+3+1 & 2\\
  6+2 & 1.
\end{array}
$$
\end{theorem}
\begin{proof}
Choose three free bit positions and fix the remaining three bits, giving
$\binom{6}{3}2^{3}=160$ cubes. On each cube, decode the eight vertices
and count the translation-label multiplicities. The displayed table is
the resulting finite spectrum.
\end{proof}

\begin{corollary}[Phe/Leu is the unique $6+2$ cube]
\label{cor:philosophy-phe-leu-unique-six-two-cube}
The unique $6+2$ cube is
$$
  \{\mathrm{UUU},\mathrm{UUC},\mathrm{UUA},\mathrm{UUG},
    \mathrm{CUU},\mathrm{CUC},\mathrm{CUA},\mathrm{CUG}\},
$$
with $\{\mathrm{UUU},\mathrm{UUC}\}=\mathrm{Phe}$ and the remaining
six codons classified as $\mathrm{Leu}$.
\end{corollary}
\begin{proof}
The exhaustive $Q_{3}$ enumeration in
\autoref{thm:philosophy-standard-code-q-three-cube-spectrum} contains
one cube of type $6+2$. Its vertices are the displayed Phe/Leu support.
\end{proof}

\begin{theorem}[Neighborhoods of the complete control tiles]
\label{thm:philosophy-complete-control-tile-q-three-neighborhoods}
The Stop/Trp tile is contained in four axis-aligned $Q_{3}$ cubes, and
all four have pattern $3+2+2+1$. The Ile/Met tile is contained in four
axis-aligned $Q_{3}$ cubes; two have pattern $3+2+2+1$, and two have
pattern $4+3+1$.
\end{theorem}
\begin{proof}
Every $Q_{2}$ face in $Q_{6}$ has four one-bit extensions to a $Q_{3}$
cube. Enumerating those four extensions for the Stop/Trp face gives
four cubes whose labels are
$$
  \mathrm{Stop}_{3}+\mathrm{Trp}_{1}
  +\text{doubleton}+\text{doubleton}.
$$
Enumerating the four extensions for the Ile/Met face gives two cubes of
the same $3+2+2+1$ form and two cubes of the form
$$
  \text{quadrupleton}+\mathrm{Ile}_{3}+\mathrm{Met}_{1}.
$$
\end{proof}

\begin{corollary}[Control-tile neighborhood contrast]
\label{cor:philosophy-control-tile-neighborhood-contrast}
The Stop/Trp tile is locally isolated as a boundary/continuation tile in
all of its $Q_{3}$ neighborhoods. The Ile/Met tile retains the same
$11$-corner control form, but two of its $Q_{3}$ neighborhoods embed it
beside a four-codon sense block.
\end{corollary}
\begin{proof}
This is the distinction between the two neighborhood spectra in
\autoref{thm:philosophy-complete-control-tile-q-three-neighborhoods}.
\end{proof}
