\begin{definition}[Private and shared coordinates]
\label{def:philosophy-private-shared-coordinates}
Let $A=\{S_{1},\ldots,S_{m}\}$ be a quotient-level support family on
$\Omega$. The private coordinate set of $S_{i}$ is
$$
  P_{i}
  =
  S_{i}\setminus\bigcup_{j\neq i}S_{j}.
$$
The shared coordinate set is
$$
  H
  =
  \Omega\setminus\bigcup_{i=1}^{m}P_{i}.
$$
For $a\in H$, write
$$
  R_{a}=\{i:a\in S_{i}\}.
$$
\end{definition}

\begin{theorem}[Private-shared decomposition]
\label{thm:philosophy-private-shared-decomposition}
A quotient-level minimal full trigger of size $m$ is equivalently the
following data:
$$
  H\subseteq\Omega,
$$
a partition of the complement into nonempty private blocks
$$
  \Omega\setminus H=P_{1}\sqcup\cdots\sqcup P_{m},
$$
and, for each $a\in H$, a row set
$$
  R_{a}\subseteq\{P_{1},\ldots,P_{m}\},
  \qquad
  |R_{a}|\geq2.
$$
The support corresponding to a private block $P$ is recovered by
$$
  S_{P}
  =
  P
  \cup
  \{a\in H:P\in R_{a}\}.
$$
This decomposition is unique.
\end{theorem}
\begin{proof}
Given a minimal full trigger, every coordinate has a well-defined
multiplicity among the supports. If the multiplicity is one, the
coordinate belongs to the unique private block attached to its support.
If the
multiplicity is at least two, the coordinate lies in $H$ and has the
unique set of private blocks whose supports contain it. Minimality gives
every private block nonempty by
\autoref{thm:philosophy-private-coordinate-criterion}.

Conversely, the displayed data define supports $S_{P}$ whose union is
$\Omega$. Since every $P_{i}$ is nonempty, each $S_{i}$ has a private
coordinate, so the family is a minimal full trigger. The construction
also proves uniqueness.
\end{proof}

\begin{theorem}[Decoration enumeration]
\label{thm:philosophy-private-shared-decoration-enumeration}
The number of quotient-level size-$m$ minimal full triggers on $n$
trigger coordinates is
$$
  C(n,m)
  =
  \sum_{h=0}^{n-m}
  \binom{n}{h}
  S(n-h,m)
  (2^{m}-m-1)^{h},
$$
where $S(n-h,m)$ is the Stirling number of the second kind.
\end{theorem}
\begin{proof}
Choose the $h$ shared coordinates in $\binom{n}{h}$ ways. Partition the
remaining $n-h$ private coordinates into $m$ nonempty private blocks in
$S(n-h,m)$ ways. For each shared coordinate, choose a row set of size at
least two. The number of such row sets is
$$
  \sum_{r=2}^{m}\binom{m}{r}
  =
  2^{m}-m-1.
$$
Summing over all possible $h$ gives the formula.
\end{proof}

\begin{corollary}[Codon counts from decorated partitions]
\label{cor:philosophy-codon-counts-decorated-partitions}
For $n=4$, the decoration formula gives
$$
  C(4,1)=1,
  \qquad
  C(4,2)=25,
  \qquad
  C(4,3)=22,
  \qquad
  C(4,4)=1.
$$
With two $f_{3}$-lifts per support, the codon-level counts are
$$
  2,\quad100,\quad176,\quad16.
$$
\end{corollary}
\begin{proof}
For $m=2$, the shared coordinate has only one possible row set, so
$$
  C(4,2)
  =
  S(4,2)+4S(3,2)+6S(2,2)
  =
  7+12+6.
$$
For $m=3$, one shared coordinate has four possible row sets, giving
$$
  C(4,3)
  =
  S(4,3)+4S(3,3)\cdot4
  =
  6+16.
$$
The cases $m=1$ and $m=4$ have no shared coordinates. Multiplying the
size-$m$ quotient count by $2^{m}$ gives the codon counts.
\end{proof}

\begin{theorem}[Defect from shared coordinates]
\label{thm:philosophy-defect-from-shared-coordinates}
For a minimal full trigger with private-shared decomposition, the
overlap defect is
$$
  \delta(A)
  =
  \sum_{a\in H}(|R_{a}|-1).
$$
\end{theorem}
\begin{proof}
Private coordinates contribute one occurrence and hence no excess over
the four-coordinate cover. A shared coordinate $a$ appears in $|R_{a}|$
supports, while one occurrence would suffice for coverage. Its excess
contribution is therefore $|R_{a}|-1$. Summing over shared coordinates
gives the formula.
\end{proof}

\begin{theorem}[Defect-refined decoration polynomial]
\label{thm:philosophy-defect-refined-decoration-polynomial}
Put
$$
  A_{m}(y)
  =
  \sum_{r=2}^{m}\binom{m}{r}y^{r-1}.
$$
Then the quotient-level defect polynomial for size-$m$ minimal triggers
on $n$ coordinates is
$$
  D_{n,m}(y)
  =
  \sum_{h=0}^{n-m}
  \binom{n}{h}
  S(n-h,m)
  A_{m}(y)^{h}.
$$
\end{theorem}
\begin{proof}
For a shared coordinate, choosing a row set of size $r$ contributes
defect $r-1$ and can be done in $\binom{m}{r}$ ways. Thus the defect
enumerator for one shared coordinate is $A_{m}(y)$. The remaining
choices are exactly those counted in
\autoref{thm:philosophy-private-shared-decoration-enumeration}.
\end{proof}

\begin{corollary}[Codon defect polynomials]
\label{cor:philosophy-codon-defect-polynomials}
For $n=4$,
$$
  D_{4,2}(y)=7+12y+6y^{2},
$$
and
$$
  D_{4,3}(y)=6+12y+4y^{2}.
$$
Together with the $m=1$ and $m=4$ singleton terms, this gives quotient
defect counts
$$
  \delta=0:15,
  \qquad
  \delta=1:24,
  \qquad
  \delta=2:10.
$$
After the two-lift codon factor, the counts are
$$
  94,\quad144,\quad56.
$$
\end{corollary}
\begin{proof}
For $m=2$, $A_{2}(y)=y$, so
$$
  D_{4,2}(y)=7+12y+6y^{2}.
$$
For $m=3$, $A_{3}(y)=3y+y^{2}$, so
$$
  D_{4,3}(y)=6+4(3y+y^{2}).
$$
The codon counts are obtained by multiplying the size-$m$ quotient
terms by $2^{m}$.
\end{proof}

\begin{corollary}[Orbit decoration table]
\label{cor:philosophy-orbit-decoration-table}
The nine orbit normal forms have the following private and shared
decoration data:
$$
\begin{array}{c|c|c}
  \text{normal form} & \text{private blocks} & \text{shared data}\\
  \hline
  \{1234\} & \{1234\} & \varnothing\\
  \{1,234\} & \{1\},\{234\} & \varnothing\\
  \{12,34\} & \{12\},\{34\} & \varnothing\\
  \{12,234\} & \{1\},\{34\} & 2:\{1,2\}\\
  \{123,124\} & \{3\},\{4\} & 1:\{1,2\},\ 2:\{1,2\}\\
  \{1,2,34\} & \{1\},\{2\},\{34\} & \varnothing\\
  \{1,24,34\} & \{1\},\{2\},\{3\} & 4:\{2,3\}\\
  \{14,24,34\} & \{1\},\{2\},\{3\} & 4:\{1,2,3\}\\
  \{1,2,3,4\} & \{1\},\{2\},\{3\},\{4\} & \varnothing.
\end{array}
$$
\end{corollary}
\begin{proof}
For each normal form, read off coordinates of multiplicity one as
private blocks and coordinates of multiplicity at least two as shared
decorations with their row sets.
\end{proof}

\begin{theorem}[Private-shared decoration theorem]
\label{thm:philosophy-private-shared-decoration-theorem}
Post-$M^{\star}$ quotient-level minimal full triggers are decorated set
partitions: a nonempty private partition of the non-shared coordinates,
plus shared coordinates decorated by row sets of size at least two.
For $n$ coordinates and $\ell$ lifts per support, the lifted size-$m$
count is
$$
  \ell^{m}
  \sum_{h=0}^{n-m}
  \binom{n}{h}
  S(n-h,m)
  (2^{m}-m-1)^{h}.
$$
The defect-refined quotient polynomial is
$$
  \sum_{h=0}^{n-m}
  \binom{n}{h}
  S(n-h,m)
  \left(\sum_{r=2}^{m}\binom{m}{r}y^{r-1}\right)^{h}.
$$
\end{theorem}
\begin{proof}
The decomposition is
\autoref{thm:philosophy-private-shared-decomposition}; the enumeration
and defect formulas are
\autoref{thm:philosophy-private-shared-decoration-enumeration} and
\autoref{thm:philosophy-defect-refined-decoration-polynomial}. The lift
factor is $\ell^{m}$ because each support in a size-$m$ quotient trigger
has $\ell$ independent lift choices.
\end{proof}
