\begin{definition}[Unary BHist indexed topology source]
\label{def:topology-unary-bhist-source}
The unary $\mathsf{BHist}$ indexed topology source for $\TopologyUp$ fixes the point object to the BEDC history carrier together with the unary carrier predicate
$$
C_{\mathsf{un}}(x):\Longleftrightarrow \UnaryHistory(x).
$$
Its carrier classifier is the history classifier $\hsame(x,y)$ restricted to points satisfying $C_{\mathsf{un}}$. The source data are an index object $\mathsf{OpenIx}_{\mathsf{un}}$, a displayed membership predicate
$$
\mathsf{OpenAt}_{\mathsf{un}}:\mathsf{OpenIx}_{\mathsf{un}}\times\mathsf{BHist}\to\mathsf{Prop},
$$
a meet operation $i,j\mapsto i\wedge_{\TopologyUp}j$, indexed arbitrary-union witnesses, boundary indices $\bot_{\TopologyUp}$ and $\top_{\TopologyUp}$, and visible $\mathsf{BHist}$ ledger rows for each admitted open.

The fields satisfy the indexed-open laws of \autoref{def:topology-indexed-open-carrier} on unary points: every $\mathsf{OpenAt}_{\mathsf{un}}(i,-)$ transports along $\hsame$, the meet index carries pointwise conjunction, the union witness carries pointwise indexed union, and the boundary indices carry the empty and whole unary predicates. A public open row is admitted only with a carried index and a ledger constructor naming one of the six rows of \autoref{def:topology-public-open-row}.
\end{definition}

\begin{theorem}[Unary indexed membership transport]
\label{thm:topology-unary-membership-transport-obligation}
Let $\mathcal{U}$ be the unary $\mathsf{BHist}$ indexed topology source of \autoref{def:topology-unary-bhist-source}. If an index $i:\mathsf{OpenIx}_{\mathsf{un}}$ carries a public unary predicate $U:\mathsf{BHist}\to\mathsf{Prop}$, then for all histories $x,y:\mathsf{BHist}$,
$$
\UnaryHistory(x)
\Longrightarrow
\UnaryHistory(y)
\Longrightarrow
\hsame(x,y)
\Longrightarrow
\bigl(U(x)\Longleftrightarrow U(y)\bigr).
$$
\end{theorem}
\begin{proof}
Assume the two unary carrier witnesses, the classifier witness $\hsame(x,y)$, and a carrying equation $h_i:\mathsf{CarriesOpen}_{\mathcal{U}}(i,U)$. The definition of the unary source says that the classifier of the indexed topology carrier is exactly the restricted $\hsame$ route on $\mathsf{BHist}$.

Unfold the carrying equation at $x$ and $y$. It converts $U(x)$ and $U(y)$ into $\mathsf{OpenAt}_{\mathsf{un}}(i,x)$ and $\mathsf{OpenAt}_{\mathsf{un}}(i,y)$.

The membership-stability field in \autoref{def:topology-unary-bhist-source}, read as the indexed-open stability field of \autoref{def:topology-indexed-open-carrier}, transports $\mathsf{OpenAt}_{\mathsf{un}}(i,-)$ along the displayed $\hsame(x,y)$ witness. Composing the two carrying equations with this transport gives the stated membership equivalence for $U$.
\end{proof}
\leanchecked{BEDC.Derived.TopologyUp.BHistPublicOpenTree\_unary\_membership\_transport}

\begin{theorem}[Unary topology constructor ledger coverage]
\label{thm:topology-unary-constructor-ledger-coverage}
For the unary $\mathsf{BHist}$ indexed topology source of \autoref{def:topology-unary-bhist-source}, every admitted unary indexed open is carried by exactly one visible constructor row among singleton metric ball, finite-list intersection, binary generated-open meet, arbitrary union, bottom, or top. The row exposes its carried index, its pointwise carrying equation, and its $\mathsf{BHist}$ provenance tag.
\end{theorem}
\begin{proof}
Unfold the admission clause in \autoref{def:topology-unary-bhist-source}. It accepts a public unary open only as a topology public open row in the sense of \autoref{def:topology-public-open-row}, so an admitted row already contains an index, a carrying equation, and a ledger constructor.

The constructor alternatives are the six alternatives listed in \autoref{def:topology-public-open-row}. Metric-generated singleton and finite-list rows are the coverage rows of \autoref{thm:topology-metric-generated-public-open-row-coverage}. Singleton bottom, top, meet, and union rows are the coverage rows of \autoref{thm:topology-singleton-public-open-row-coverage}.

For composite rows, the downstream coverage theorem \autoref{thm:topology-downstream-open-constructor-coverage} identifies the same six constructor names and rules out any unindexed open predicate. Since the unary source records the constructor as a visible tagged ledger row, two different constructor names are not the same row of the source ledger; hence each admitted unary open has exactly the displayed row that introduced it.
\end{proof}
\leanchecked{BEDC.Derived.TopologyUp.BHistUnaryTopologyLedgerRow\_constructor\_coverage}

\begin{theorem}[Unary topology ledger constructor no-confusion]
\label{thm:topology-unary-ledger-constructor-no-confusion}
Let $\mathcal{U}$ be the unary $\mathsf{BHist}$ indexed topology source of \autoref{def:topology-unary-bhist-source}. For any unary public predicate $U:\mathsf{BHist}\to\mathsf{Prop}$ carried by an admitted visible $\mathsf{BHistUnaryTopologyLedgerRow}$, no row introduced by one of
$$
\mathsf{singletonMetricBall},\quad
\mathsf{finiteListIntersection},\quad
\mathsf{binaryGeneratedMeet},\quad
\mathsf{arbitraryUnion},\quad
\mathsf{bottom},\quad
\mathsf{top}
$$
can also be introduced by a different named constructor from the same list while carrying the same predicate $U$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:topology-unary-constructor-ledger-coverage} to reduce an admitted unary row to the six visible constructor alternatives listed in the statement. The closed inductive row type $\mathsf{BHistUnaryTopologyLedgerRow}$ has no additional public-open row form, so every admissible branch has one exposed outer constructor.

Now invert the exposed constructor of the row. In the $\mathsf{singletonMetricBall}$ branch, constructor inversion rejects equality with each of the finite-list, binary-meet, arbitrary-union, bottom, and top branches. The same inversion argument applies to each remaining branch, because the outer constructor name is the first datum recovered from the closed ledger row before any carried index or pointwise carrying equation is read.

Thus two derivations of the same visible row carrying the same predicate $U$ must expose the same constructor name. If the names are different, constructor no-confusion for the closed inductive ledger gives a contradiction, so an admitted unary row cannot have two different visible constructor origins.
\end{proof}
\leanchecked{BEDC.Derived.TopologyUp.BHistUnaryTopologyLedgerRow\_constructor\_tag\_no\_confusion}

\begin{theorem}[Unary BHist topology public certificate]
\label{thm:topology-unary-bhist-public-certificate}
Let $\mathcal{U}$ be the unary $\mathsf{BHist}$ indexed topology source of \autoref{def:topology-unary-bhist-source}. Any visible $\mathsf{BHistUnaryTopologyLedgerRow}$ carrying a nonempty unary public predicate $U$ exports a $\mathsf{SemanticNameCert}$ whose carrier is $\UnaryHistory(h)\land U(h)$, whose pattern is $\mathsf{OpenAt}_{\mathsf{un}}(i,h)$, whose ledger records a unary $\mathsf{BHist}$ constructor row together with the carried index membership, and whose classifier is $\UnaryHistory(h)\land\UnaryHistory(k)\land\hsame(h,k)$.
\end{theorem}
\leanchecked{BEDC.Derived.TopologyUp.BHistUnaryTopologyLedgerRow\_semantic\_name\_certificate}
\begin{proof}
Use \autoref{thm:topology-unary-constructor-ledger-coverage} to split the visible ledger row into its six possible constructors: singleton metric ball, finite-list intersection, binary generated-open meet, arbitrary union, bottom, and top. In each branch the row supplies the same carried index $i$, a pointwise carrying equation between $U$ and $\mathsf{OpenAt}_{\mathsf{un}}(i,-)$ on unary histories, and the displayed $\mathsf{BHist}$ provenance tag.

The source witness for nonempty $U$ gives the inhabited carrier clause for $\UnaryHistory(h)\land U(h)$. Reflexivity, symmetry, and transitivity of the certificate classifier are the corresponding $\hsame$ rules restricted to unary histories.

For carrier transport, apply \autoref{thm:topology-unary-membership-transport-obligation}. The carrying equation converts a carrier point of $U$ into indexed-open membership at $i$, the source transport moves that membership along $\hsame$, and the carried-index equation converts it back to $U$ at the target unary history.

Pattern soundness is the forward direction of the same carried-index equation. Ledger soundness packages the constructor branch selected above, the recorded unary provenance tag, and the indexed membership just obtained from the carrying equation. Thus every admitted unary public row exports the stated semantic certificate without adding an unindexed open predicate.
\end{proof}

\begin{theorem}[Topology deps-ready obligation package]
\label{thm:topology-deps-ready-obligation-package}
The unary $\mathsf{BHist}$ source of \autoref{def:topology-unary-bhist-source}, the transport theorem \autoref{thm:topology-unary-membership-transport-obligation}, the ledger coverage theorem \autoref{thm:topology-unary-constructor-ledger-coverage}, and the finite-intersection, arbitrary-union, and boundary closure theorems
$$
\autoref{thm:topology-indexed-open-finite-intersection},\qquad
\autoref{thm:topology-indexed-open-arbitrary-union},\qquad
\autoref{thm:topology-indexed-open-boundary-closure}
$$
assemble the paper-side $\TopologyUp$ obligation package consumed by $\ContinuousMapUp$, $\BanachUp$, $\ManifoldUp$, and $\ComplexTopologyUp$. A downstream consumer receives only the unary carrier $C_{\mathsf{un}}$, the restricted $\hsame$ classifier, a carried-open index, the carrying equation, the finite-intersection and arbitrary-union constructors, the boundary constructors, and the visible constructor ledger.
\end{theorem}
\leanchecked{BEDC.Derived.TopologyUp.BHistUnaryTopologyDepsReady\_obligation\_package}
\begin{proof}
The source definition fixes the downstream carrier and classifier: points are $\mathsf{BHist}$ histories satisfying $\UnaryHistory$, and all point transport is through the restricted $\hsame$ classifier. The theorem \autoref{thm:topology-unary-membership-transport-obligation} is the exported membership-transport rule for every carried unary open.

Closure under finite intersections is the indexed-open theorem \autoref{thm:topology-indexed-open-finite-intersection}. Closure under arbitrary unions is \autoref{thm:topology-indexed-open-arbitrary-union}. Boundary opens are supplied by \autoref{thm:topology-indexed-open-boundary-closure}. These three theorems operate on the same carried-index interface named in the unary source.

It remains to identify the public provenance that dependent chapters may cite. The coverage theorem \autoref{thm:topology-unary-constructor-ledger-coverage} restricts every admitted unary open to one visible constructor row, while \autoref{thm:topology-downstream-open-constructor-coverage} and the metric-generated and singleton coverage rows identify the same constructor list on the exported topology surface.

Combining these fields gives the advertised obligation package. Continuous maps use the transported membership row for preimage obligations; Banach and manifold certificates use the carried-open closure rows for neighbourhood and chart domains; the complex-topology certificate uses the same unary-carried interface for its topological side. No clause constructs a standard topological-space object or replaces $\hsame$ by host equality.
\end{proof}
