\chapter{A Concrete Naming Certificate for $\BHistHendecaTupleNameCertUp$}
\label{ch:concrete-instances-b-hist-hendeca-tuple-namecert}
\origin{ai}

The $\BHistHendecaTupleNameCertUp$ packet is the arity-eleven capstone for the carrier-isomorphism bucket already exhibited by the neighboring tuple chapters \autoref{ch:concrete-instances-b-hist-octa-tuple-name-cert-namecert}, \autoref{ch:concrete-instances-b-hist-nona-tuple-name-cert-namecert}, and \autoref{ch:concrete-instances-b-hist-deca-tuple-name-cert-namecert}. It is composite over the same bucket anchors: the anchor-stability certificate of \autoref{ch:concrete-instances-anchor-stability-certificate-namecert}, the audit-map family of \autoref{ch:concrete-instances-auditmapfamily-namecert}, the BEDC self-substrate packet of \autoref{ch:concrete-instances-bedc-self-substrate-namecert}, the apophatic fixed-point fiber of \autoref{ch:concrete-instances-apophatic-fixed-point-fiber-namecert}, and the beta critical-pair packet of \autoref{ch:concrete-instances-beta-critical-pair-namecert}. The chapter gives the eleven-row carrier a single BEDC name so downstream consumers can cite the tag, comparison, transport, replay, provenance, and local-name surface without treating any bucket member as a replacement for another.

\begin{definition}[BHistHendecaTupleNameCert carrier]
\label{def:b-hist-hendeca-tuple-name-cert-carrier}
A $\BHistHendecaTupleNameCertUp$ carrier is a finite $\BHist$ packet
$$
E=(R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $R_0,\ldots,R_{10}$ are the eleven tag-encoded carrier rows. Each row is a $\BHist$ entry whose tag records the local carrier role used by a cited bucket sibling and whose payload is read only as a displayed BEDC history component.
\item $H$ records componentwise $\hsame$ transport for $R_0,\ldots,R_{10},C,P,L$ and no transport row outside the displayed packet.
\item $C$ records the displayed $\Cont$ route that replays row admission, componentwise comparison, transport, provenance readback, and local naming for the same eleven-row packet.
\item $P$ is the $\Pkg$ provenance over the arity-eleven tag encoder, the cited sibling carrier families, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $L$ is the local $\NameCert_{\BHistHendecaTupleNameCertUp}$ row.
\end{enumerate}
The carrier has no coordinate for an untagged row, a twelfth carrier component, a host-side equality test, a bucket-wide rewrite of sibling chapters, or a detached provenance table.
\end{definition}

\begin{definition}[BHistHendecaTupleNameCert classifier]
\label{def:b-hist-hendeca-tuple-name-cert-classifier}
Two $\BHistHendecaTupleNameCertUp$ packets
$$
E=(R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},H,C,P,L)
$$
and
$$
E'=(R'_0,R'_1,R'_2,R'_3,R'_4,R'_5,R'_6,R'_7,R'_8,R'_9,R'_{10},H',C',P',L')
$$
are classifier-equivalent exactly when each displayed carrier row compares componentwise,
$$
\begin{aligned}
&R_0 \sim R'_0,\quad R_1 \sim R'_1,\quad R_2 \sim R'_2,\quad R_3 \sim R'_3,\quad R_4 \sim R'_4,\quad R_5 \sim R'_5,\\
&R_6 \sim R'_6,\quad R_7 \sim R'_7,\quad R_8 \sim R'_8,\quad R_9 \sim R'_9,\quad R_{10} \sim R'_{10},
\end{aligned}
$$
the transport rows display the same $\hsame$ routes for those components and for $C,P,L$, and the replay rows display the same $\Cont$ route from row admission through local naming. No comparison is available through an omitted component, an untagged payload, or a member-chapter rewrite.
\end{definition}

\begin{theorem}[BHistHendecaTupleNameCert obligations]
\label{thm:b-hist-hendeca-tuple-name-cert-obligations}
Every accepted $\BHistHendecaTupleNameCertUp$ packet admits exactly the carrier rows
$$
R_0,R_1,R_2,R_3,R_4,R_5,R_6,R_7,R_8,R_9,R_{10},H,C,P,L,
$$
and its classifier is exact for that arity-eleven carrier surface. The eleven rows are tag-encoded $\BHist$ components, and $H,C,P,L$ are the only structural rows by which a consumer may transport, replay, source, or locally name the packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:b-hist-hendeca-tuple-name-cert-carrier}. The definition lists the eleven tag-encoded $\BHist$ rows and then lists the transport, continuation, provenance, and local naming rows.

Next read the classifier in \autoref{def:b-hist-hendeca-tuple-name-cert-classifier}. It requires one comparison for each displayed carrier row and then uses the same row list for $\hsame$ transport, $\Cont$ replay, provenance, and local naming.

There is no remaining coordinate in the packet. Thus any accepted carrier read lands in exactly the displayed rows, and any proposed twelfth component, detached structural table, host equality test, or bucket-membership comparison lies outside the accepted surface.
\end{proof}

\begin{theorem}[BHistHendecaTuple tag exhaustion]
\label{thm:b-hist-hendeca-tuple-tag-exhaustion}
For a $\BHistHendecaTupleNameCertUp$ packet, the tags carried by $R_0,\ldots,R_{10}$ exhaust the carrier rows available to the local $\NameCert$ interface. A consumer may permute or replay the displayed rows only through the named $\hsame$ and $\Cont$ rows $H$ and $C$; it may not manufacture an unlisted tag, collapse two tags into one bucket witness, or import an additional row from a sibling chapter.
\end{theorem}
\begin{proof}
The local $\NameCert_{\BHistHendecaTupleNameCertUp}$ row $L$ is part of the displayed carrier, so its reads are bounded by the carrier coordinates named in \autoref{def:b-hist-hendeca-tuple-name-cert-carrier}. Those coordinates contain exactly the eleven tagged $\BHist$ rows and the structural rows $H,C,P,L$.

The classifier in \autoref{def:b-hist-hendeca-tuple-name-cert-classifier} repeats the same eleven tags and gives no rule for an omitted tag or a collapsed bucket witness. Transport and replay therefore preserve the displayed tag list rather than extending it.
\end{proof}
\leanchecked{BEDC.Derived.BHistHendecaTupleNameCertUp.BHistHendecaTupleTagExhaustion}

\falsifiablePrediction{Any accepted consumer route that reads an untagged row, a twelfth carrier row, or bucket membership alone fails carrier admission, classifier exactness, or tag exhaustion for $\BHistHendecaTupleNameCertUp$.}

\independenceWitness{b-hist-octa-tuple-name-cert, b-hist-nona-tuple-name-cert, b-hist-deca-tuple-name-cert, and the cited bucket siblings: none is bijective to $\BHistHendecaTupleNameCertUp$ because this packet carries eleven tagged rows together with transport, replay, provenance, and local $\NameCert$ in one packet, while the neighboring capstones carry different arities and each sibling supplies only a member-family surface.}

\closureat{BHistHendecaTupleNameCertUp}{seedStr}

\begin{closurestatus}{\BHistHendecaTupleNameCertUp}
  \constructivestory{A $\BHistHendecaTupleNameCertUp$ packet is generated from eleven tag-encoded $\BHist$ carrier rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:b-hist-hendeca-tuple-name-cert-carrier}, \autoref{def:b-hist-hendeca-tuple-name-cert-classifier}, \autoref{thm:b-hist-hendeca-tuple-name-cert-obligations}, and \autoref{thm:b-hist-hendeca-tuple-tag-exhaustion} identify the arity-eleven carrier-isomorphism surface and its BEDC support package.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not provide a Lean declaration, standard bridge, member-chapter replacement, or public acceptance interface.}
  \upgradepath{Formalization requires a Lean carrier for BEDC.Derived.BHistHendecaTupleNameCertUp and checked carrier-obligation plus tag-exhaustion theorems.}
\end{closurestatus}
