\chapter{Dyadic Interval Net NameCert Construction}
\label{ch:concrete-instances-dyadic-interval-net-namecert}
\origin{human}

Following Bishop and Bridges, the $\DyadicIntervalNetUp$ packet records finite dyadic interval nets as the displayed cover primitive used by Real and Completion arguments before any consumer may invoke compactness language. It sits after the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite StreamName windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. As a consumer route, the finite interval-cell row consumes dyadic endpoint arithmetic from \autoref{ch:concrete-instances-dyadicratcore-namecert}, exposes endpoint observations through \autoref{ch:concrete-instances-streamname-namecert}, reads tolerances through \autoref{ch:concrete-instances-regseqrat-namecert}, and seals only through \autoref{ch:concrete-instances-real-namecert}. The packet gives compact-interval, completion, and uniform-modulus consumers a finite cover surface; it does not assert open-cover compactness, selected subcovers, quotient stream equality, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Dyadic interval net carrier]\label{def:dyadic-interval-net-carrier}
A $\DyadicIntervalNetUp$ carrier is a finite $\BHist$ packet
$$
I=(D,J,E,S,R,Q,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ endpoint row. It lists the dyadic endpoints, midpoint and radius arithmetic, and successor comparisons used by the net cells.
\item $J$ is the finite interval-cell row. It records a finite list of closed dyadic cells, each with displayed left and right endpoints and a cell radius.
\item $E$ is the endpoint-incidence row. It records that adjacent cells overlap or touch at displayed dyadic endpoints and that the first and last cells bracket the named interval endpoints.
\item $S$ is the $\StreamNameUp$ window row exposed when an interval endpoint or cell endpoint is read.
\item $R$ is the $\RegSeqRatUp$ readback row for the dyadic endpoints and the tolerance schedule induced by the cell radii.
\item $Q$ is the terminal $\RealUp$ seal row reached only after the displayed StreamName and RegSeqRat rows have been inspected.
\item $H$ records componentwise $\hsame$ transport for $D,J,E,S,R,Q$ and the structural rows.
\item $C$ records displayed $\Cont$ replay of the finite route
$$
D,J,E \longmapsto S,R \longmapsto Q,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\DyadicIntervalNetUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\DyadicIntervalNetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,J,E,S,R,Q,H,C,P,N$. It has no coordinate for an arbitrary open cover, a selected finite subcover, quotient stream equality, a chosen limit point, countable choice, trichotomy, or completed real compactness.
\end{definition}

\begin{theorem}[Dyadic interval net cover refinement]\label{thm:dyadic-interval-net-cover-refinement}
For every accepted $\DyadicIntervalNetUp$ carrier $I=(D,J,E,S,R,Q,H,C,P,N)$, every Real and Completion consumer that reads a finite dyadic cover through $I$ factors through the finite route
$$
D,J,E \longmapsto S,R \longmapsto Q .
$$
The interval-cell row $J$ and endpoint-incidence row $E$ refine any displayed dyadic cover request into listed dyadic cells whose endpoints and radii are checked in $D$, whose inspected name coordinates are exposed in $S$, whose tolerance schedule is read in $R$, and whose Real boundary is sealed in $Q$. No open-cover compactness, selected subcover, quotient stream equality, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness is available along this route.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:dyadic-interval-net-carrier}. The rows $D,J,E$ are the only cover-facing data: $D$ supplies dyadic endpoint arithmetic, $J$ supplies the finite list of cells, and $E$ supplies endpoint incidence and bracketing.

The refinement is therefore a finite list operation. A displayed cover request is answered by reading the listed cells in $J$, checking their dyadic radii and endpoint comparisons in $D$, and using $E$ to verify that adjacent cells cover the named interval without opening a host compactness argument.

The Real-facing portion is delayed. The inspected endpoint names pass through $S$, the induced tolerance schedule passes through $R$, and the terminal real-name boundary is exposed only by $Q$.

Finally replay $H,C,P,N$. Transport, continuation replay, provenance, and local naming preserve exactly the same finite route, so the consumer cannot replace the dyadic net by a selected subcover, quotient stream equality, choice, trichotomy, host equality, or ambient completeness principle.
\end{proof}

The same finite-cell surface is consumed by the compact interval uniform-modulus route of \autoref{ch:concrete-instances-compact-interval-uniform-modulus-namecert}. A downstream consumer reads the $\DyadicRatCoreUp$ endpoint row, the $\StreamNameUp$ window row, the $\RegSeqRatUp$ tolerance row, and the terminal $\RealUp$ seal in the displayed order, so the interval net remains a finite cover handoff rather than an open-cover compactness principle.

\begin{theorem}[Dyadic interval net obligation surface]\label{thm:dyadic-interval-net-obligation-surface}
For every accepted $\DyadicIntervalNetUp$ carrier $I=(D,J,E,S,R,Q,H,C,P,N)$, carrier admission and cell coverage are exhausted by the displayed rows $D,J,E,H,C,P,N$. The endpoint arithmetic, finite interval-cell list, endpoint incidence, componentwise transport, replay, provenance, and local naming rows supply the complete finite obligation surface for a dyadic net request, and no open-cover compactness or selected finite subcover is exported.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-interval-net-carrier}. The rows $D,J,E$ display the endpoint arithmetic, listed cells, and incidence witnesses, while $H,C,P,N$ transport, replay, source, and name those rows.

Cell coverage is therefore a finite row check. Each requested interval read is matched with cells already listed in $J$, the endpoint comparisons already listed in $D$, and the bracketing and adjacency data already listed in $E$.

The structural rows do not add a second cover object. They preserve the displayed packet componentwise, so no open cover, selected subcover, choice principle, or ambient compactness row can enter the obligation surface.
\end{proof}

\begin{theorem}[Dyadic interval net StreamName and RegSeqRat handoff]\label{thm:dyadic-interval-net-streamname-regseqrat-handoff}
Every downstream consumer of an accepted $\DyadicIntervalNetUp$ carrier that inspects interval endpoints or cell tolerances must factor the read through
$$
D,J,E \longmapsto S,R \longmapsto H,C,P,N .
$$
The $\StreamNameUp$ row $S$ exposes the finite endpoint windows and the $\RegSeqRatUp$ row $R$ exposes the rational tolerance readback; neither row may be skipped or replaced by quotient stream equality, selected limits, or countable choice.
\end{theorem}
\begin{proof}
Start from a downstream endpoint or tolerance read. By the carrier definition, the only cover-facing rows available before the read are $D,J,E$, so the requested endpoint or cell radius is first located inside the displayed dyadic net.

The read then passes through $S$ and $R$. The StreamName row supplies finite observation windows for the endpoint names, and the RegSeqRat row supplies the regular rational schedule attached to those observations.

Finally replay $H,C,P,N$. Componentwise transport, continuation replay, provenance, and local naming keep the same finite handoff visible to the consumer, excluding quotient stream equality, selected limits, and choice.
\end{proof}

\begin{theorem}[Dyadic interval net Real seal nonescape]\label{thm:dyadic-interval-net-real-seal-nonescape}
For every accepted $\DyadicIntervalNetUp$ carrier $I=(D,J,E,S,R,Q,H,C,P,N)$, the terminal $\RealUp$ seal row $Q$ is reachable only after the finite dyadic net route
$$
D,J,E \longmapsto S,R
$$
has been displayed. Any Real or Completion consumer that reaches $Q$ remains inside the same routed packet $D,J,E,S,R,Q,H,C,P,N$ and cannot escape to host real equality, real trichotomy, ambient $\RealUp$ completeness, selected subcovers, quotient equality, selected limits, or countable choice.
\end{theorem}
\begin{proof}
Project the accepted packet. The carrier places $Q$ downstream of the endpoint arithmetic, finite cells, endpoint incidence, StreamName windows, and RegSeqRat readback rows.

Thus a Real or Completion consumer must first traverse $D,J,E,S,R$. These rows display the cover cells, endpoint reads, and tolerance schedule before any Real-facing boundary is available.

Once $Q$ is reached, the structural rows $H,C,P,N$ only preserve the same displayed route. Since no excluded equality, selection, trichotomy, choice, or completeness row is present in the carrier, the Real seal cannot be used as an escape from the finite dyadic interval-net packet.
\end{proof}

\closureat{DyadicIntervalNetUp}{seedStr}

\begin{closurestatus}{\DyadicIntervalNetUp}
  \constructivestory{A $\DyadicIntervalNetUp$ packet is generated from dyadic endpoint arithmetic, finite interval cells, endpoint incidence, StreamName windows, RegSeqRat readback, Real seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-interval-net-carrier} and \autoref{thm:dyadic-interval-net-cover-refinement} seed the finite dyadic interval-net carrier over dyadic endpoint arithmetic, listed interval cells, endpoint incidence, StreamName windows, RegSeqRat readback, Real seals, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected subcovers, quotient stream equality, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic cell coverage, endpoint-incidence refinement, StreamName and RegSeqRat readback routing, Real seal ordering, provenance, and local naming for BEDC.Derived.DyadicIntervalNetUp.}
\end{closurestatus}
