\begin{theorem}[ContinuousMap CompleteMetric CompactMetric uniform route]
\label{thm:continuousmap-completemetric-compactmetric-uniform-route}
Let a metric $\ContinuousMapUp$ carrier have source row supplied by a $\CompactMetricUp$ certificate and target row supplied by a $\CompleteMetricUp$ certificate. Every uniform-modulus read factors through the displayed six-history ContinuousMap carrier, the $\CompactMetricUp$ total-bounded finite-net and complete-limit rows, and the $\CompleteMetricUp$ limit-witness rows.

The route exports no open-cover compactness, no choice-selected subnet, and no host function equality. It is a finite certificate route over the ContinuousMap source, map, target, modulus, certificate, distance, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows together with the compact and complete metric ledgers.
\end{theorem}
\begin{proof}
Project the ContinuousMap side through \autoref{def:continuousmapup-metric-source-specification}, \autoref{def:continuousmapup-metric-pattern-specification}, and \autoref{def:continuousmapup-metric-ledger-policy}. These rows expose exactly the six histories, the categorical graph row, the modulus row, the metric source and target rows, and the canonical endpoint-distance ledger.

Read the compact source through \autoref{thm:compactmetric-certificate-package} and \autoref{thm:compactmetric-public-export-surface}. The source contributes total-bounded finite-net rows and complete-limit witness rows over the same metric carrier, not open-cover compactness or a selected subnet.

Read the complete target through the complete-metric limit-witness surface, in particular \autoref{def:completemetric-limit-witness} and \autoref{thm:completemetric-limit-witness-stability}. These rows provide the target-side limit witness and its transport without adding a host function equality test.

Repack the ContinuousMap, CompactMetric, and CompleteMetric rows as one uniform-modulus consumer route. The visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ ledgers carry the route, so every uniform-modulus read remains finite and excludes open-cover compactness, choice-selected subnets, and host function equality.
\end{proof}

\begin{theorem}[ContinuousMap compact-complete uniform finite route sharpening]
\label{thm:continuousmap-compact-complete-uniform-route-sharpening}
Let a metric $\ContinuousMapUp$ carrier be displayed by the six histories
$source,map,target,modulus,cert,distance:\mathsf{BHist}$. Suppose the source
metric row is read through a $\CompactMetricUp$ certificate and the target
metric row is read through a $\CompleteMetricUp$ certificate. Then every
uniform-modulus consumer route factors through exactly the following finite
surface:
\begin{enumerate}
  \item the displayed ContinuousMap histories
  $source,map,target,modulus,cert,distance$;
  \item the compact finite-net rows and complete-limit rows exported by the
  $\CompactMetricUp$ source;
  \item the target complete-limit witness rows exported by
  $\CompleteMetricUp$;
  \item the $\mathsf{MetricDistanceWitness}$ row for the source-target metric
  read;
  \item componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local
  $\NameCert$ rows.
\end{enumerate}
The route exports no open-cover compactness, no selected subnet, no host
function equality, no quotient stream equality, and no ambient completeness
principle. In particular, any later compact-uniform-continuity or
Real-completion consumer reading the route receives only this finite
$\NameCert$ consumer surface.
\end{theorem}
\begin{proof}
First project the ContinuousMap carrier by
\autoref{def:continuousmapup-metric-source-specification},
\autoref{def:continuousmapup-metric-pattern-specification}, and
\autoref{def:continuousmapup-metric-ledger-policy}. These definitions expose
the six histories, the categorical graph row, the target modulus row, the
metric distance witness, the componentwise $\hsame$ classifier, displayed
$\Cont$ rows, $\Pkg$ provenance, and local $\NameCert$ bookkeeping.

Next apply
\autoref{thm:continuousmap-completemetric-compactmetric-uniform-route}. This
already forces every uniform-modulus read through the ContinuousMap carrier,
the compact finite-net and complete-limit rows, and the complete-metric
limit-witness rows, while refusing open-cover compactness, selected subnets,
and host function equality.

Read the compact coordinate through
\autoref{thm:compactmetric-certificate-package} and
\autoref{thm:compactmetric-public-export-surface}. The compact source
therefore contributes only finite-net coverage, total-bounded rows,
complete-limit rows, and their displayed metric ledgers.

Read the complete coordinate through
\autoref{def:completemetric-limit-witness} and
\autoref{thm:completemetric-limit-witness-stability}. The target contributes
only named limit witnesses, threshold rows, late-distance witnesses, and
their classifier-stable transport rows.

Finally repack the three readings as the finite consumer surface listed in
the theorem. Since each coordinate is displayed as a $\BHist$ row with its
own $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ evidence, no quotient stream
equality, ambient completeness principle, or host-level equality test can be
read from the route.
\end{proof}

\begin{theorem}[ContinuousMap compact-complete uniform route refinement]
\label{thm:continuousmap-compact-complete-uniform-route-refinement}
Let a metric $\ContinuousMapUp$ carrier be displayed by the histories
$source,map,target,modulus,cert,distance:\mathsf{BHist}$, with the source row
read through a $\CompactMetricUp$ certificate and the target row read through
a $\CompleteMetricUp$ certificate. Then every compact-complete
uniform-modulus consumer of this carrier has the exact finite surface
consisting only of:
\begin{enumerate}
  \item the six $\ContinuousMapUp$ histories
  $source,map,target,modulus,cert,distance$;
  \item the $\CompactMetricUp$ finite-net rows for the source metric;
  \item the $\CompleteMetricUp$ limit-witness rows for the target metric;
  \item the $\mathsf{MetricDistanceWitness}(source,target,distance)$ row;
  \item componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local
  $\NameCert$ rows.
\end{enumerate}
No open-cover compactness, selected subnet, quotient stream equality, or host
function equality is part of the consumer surface.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:continuousmap-completemetric-compactmetric-uniform-route}. It
places every uniform-modulus read behind the six-history $\ContinuousMapUp$
carrier, the compact metric rows, and the complete-metric limit-witness rows.

Sharpen the carrier boundary with
\autoref{thm:continuousmap-compact-complete-uniform-route-sharpening}. This
identifies the visible consumer coordinates as the displayed histories,
finite-net rows, target limit-witness rows, the source-target
$\mathsf{MetricDistanceWitness}$ row, and the componentwise $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ ledgers.

The compact coordinate is then read through
\autoref{thm:compactmetric-certificate-package} and
\autoref{thm:compactmetric-public-export-surface}. These theorems keep the
source contribution on finite-net and complete-limit rows, so an open-cover
compactness principle or selected subnet has no exported row to consume.

The target coordinate is read through
\autoref{def:completemetric-limit-witness} and
\autoref{thm:completemetric-limit-witness-stability}. The target contribution
is therefore a named limit-witness surface with stable transported rows, not
quotient stream equality or a host function equality test.

Combining these projections leaves exactly the five listed families of rows.
Every later compact-uniform or Real-completion consumer must enter through
that finite $\NameCert$ surface, and the excluded objects remain outside the
route because none of the cited certificate surfaces exports them.
\end{proof}

\begin{theorem}[ContinuousMap compact-complete uniform exact consumer surface]
\label{thm:continuousmap-compact-complete-uniform-exact-consumer-surface}
Let a displayed $\ContinuousMapUp$ carrier have histories
$source,map,target,modulus,cert,distance:\mathsf{BHist}$. Suppose the source
metric row is supplied by a $\CompactMetricUp$ certificate, the target metric
row is supplied by a $\CompleteMetricUp$ certificate, and the endpoint
distance row is displayed as
$\mathsf{MetricDistanceWitness}(source,target,distance)$. A compact-complete
uniform-modulus consumer of
$\mathsf{ContinuousMapCarrier}(source,map,target,modulus,cert,distance)$ is
accepted exactly when its finite surface consists of the following rows:
\begin{enumerate}
  \item the six displayed $\ContinuousMapUp$ histories
  $source,map,target,modulus,cert,distance$;
  \item the $\CompactMetricUp$ finite-net and complete-limit rows supplied by
  \autoref{thm:compactmetric-certificate-package} and
  \autoref{thm:compactmetric-public-export-surface};
  \item the target $\CompleteMetricUp$ limit-witness rows supplied by
  \autoref{def:completemetric-limit-witness} and
  \autoref{thm:completemetric-limit-witness-stability};
  \item the row
  $\mathsf{MetricDistanceWitness}(source,target,distance)$;
  \item componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local
  $\NameCert$ provenance for the displayed rows.
\end{enumerate}
Equivalently, every accepted consumer projects to precisely these rows, and
any display of precisely these rows repacks as the same finite
compact-complete uniform consumer surface. No open-cover compactness,
selected subnet, quotient stream equality, host function equality, or ambient
completeness principle is exported.
\end{theorem}
\begin{proof}
For the forward direction, first apply
\autoref{thm:continuousmap-completemetric-compactmetric-uniform-route}. It
places the consumer behind the six-history $\ContinuousMapUp$ carrier, the
compact source rows, and the complete target rows.

Apply
\autoref{thm:continuousmap-compact-complete-uniform-route-sharpening} and
\autoref{thm:continuousmap-compact-complete-uniform-route-refinement} to
identify the visible rows. These route theorems leave only the displayed
histories, the compact finite-net contribution, the target limit-witness
contribution, the metric-distance witness, and the componentwise $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ provenance.

The compact rows are then read through
\autoref{thm:compactmetric-certificate-package} and
\autoref{thm:compactmetric-public-export-surface}. Thus the compact source
coordinate contributes finite-net and complete-limit rows, not an open-cover
compactness principle or a selected subnet.

The target rows are read through
\autoref{def:completemetric-limit-witness} and
\autoref{thm:completemetric-limit-witness-stability}. Thus the complete
target coordinate contributes named limit-witness and stable transport rows,
not quotient stream equality, host function equality, or an ambient
completeness principle.

For the reverse direction, start from a displayed finite surface containing
exactly the five listed families of rows. The six ContinuousMap histories,
the metric-distance witness, and the componentwise $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ provenance rebuild the displayed carrier boundary.

The compact finite-net and complete-limit rows supply the source side, while
the complete limit-witness rows supply the target side. Repacking these rows
through the same three route theorems gives the compact-complete
uniform-modulus consumer and no additional exported object. Hence acceptance
is exactly the displayed finite surface.
\end{proof}

\begin{theorem}[ContinuousMap CompactMetric MetricTriangle handoff]
\label{thm:continuousmap-compactmetric-metric-triangle-handoff}
Let a metric $\ContinuousMapUp$ carrier be displayed by the six histories
$source,map,target,modulus,cert,distance:\mathsf{BHist}$. Suppose its source
row is read through a compact $\CompactMetricUp$ finite-net certificate, its
target row is read through a $\CompleteMetricUp$ limit-witness certificate,
and an accepted $\MetricTriangleUniformEstimateUp$ carrier uses the same
compact-net center, the two $\ContinuousMapUp$ pointwise target-estimate rows,
the target $\MetricUp$ triangle row, and the downstream $\UniformModulusUp$
handoff. Then the combined handoff factors through exactly the finite surface
of the six $\ContinuousMapUp$ histories, the $\CompactMetricUp$ finite-net
rows, the $\CompleteMetricUp$ target limit-witness rows, the source and target
metric-triangle rows, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ support rows.

The handoff exports no open-cover compactness, selected subnet, choice
principle, host function equality, quotient stream equality, semantic
continuity theorem, or $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:continuousmap-compact-complete-uniform-route-refinement}. It
places the ContinuousMap consumer behind the six displayed histories, the
compact finite-net source rows, the complete target limit-witness rows, the
metric distance witness, and the visible $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ ledgers.

Next read the accepted $\MetricTriangleUniformEstimateUp$ packet through
\autoref{thm:metric-triangle-uniform-estimate-public-uniformity-criterion}.
This binds the same compact-net center to the two pointwise target estimates
and to the target metric triangle row before the downstream
$\UniformModulusUp$ consumer can read the estimate.

Use
\autoref{thm:metric-triangle-uniform-estimate-consumer-boundary-package} to
identify the consumer boundary. The boundary contains the selected finite-net
center, source metric rows, pointwise target estimates, target triangle row,
and support rows, so it agrees with the ContinuousMap route on the finite
carrier data rather than on host-level functions or quotient streams.

Finally apply
\autoref{thm:metric-triangle-uniform-estimate-public-closure-package}. It
packages the public $\MetricTriangleUniformEstimateUp$ export as the same
finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface required by
the ContinuousMap refinement. Since none of the cited surfaces exports
open-cover compactness, selected subnets, choice, semantic continuity,
$\RealUp$ completeness, host function equality, or quotient stream equality,
the composed handoff cannot supply those objects to a downstream
$\UniformModulusUp$ consumer.
\end{proof}
