The quasi-uniform reflection lattice keeps completion-facing consumers downstream of directed entourage data. A $\UniformCompletionUp$ or $\SeparatedUniformSpaceUp$ reader may appear in the reflected row of a $\QuasiUniformSpaceUp$ packet, but it first reads the directed entourage rows before it can consume the uniform completion surface of \autoref{ch:concrete-instances-uniformcompletion-namecert} or the separated sibling surface.

\begin{theorem}[Uniform completion reflection lattice for quasi-uniform data]
\label{thm:quasi-uniform-space-uniform-completion-reflection-lattice}
Let $Q=(U,D,F,N,E,H,C,P,L)$ be an accepted $\QuasiUniformSpaceUp$ carrier. Every $\UniformCompletionUp$ or $\SeparatedUniformSpaceUp$ consumer named by $E$ or $P$ first reads the directed entourage row $U$ and direction ledger $D$, then the reflection row $E$, before any completion-facing or separated-uniform surface is available. Thus the reflected route through \autoref{ch:concrete-instances-uniformspace-namecert} and \autoref{ch:concrete-instances-uniformcompletion-namecert} remains downstream of finite quasi-uniform data.
\end{theorem}
\begin{proof}
Project the carrier row. The directed entourage row $U$ and direction ledger $D$ are displayed before the reflection row $E$, so a reflected consumer cannot begin with symmetric or separated completion data.

Use the uniform reflection route of \autoref{thm:quasi-uniform-space-uniform-reflection-route}. It names $\UniformSpaceUp$, $\UniformCompletionUp$, and $\SeparatedUniformSpaceUp$ only as downstream readers of the directed rows.

The structural rows $H,C,P,L$ transport, replay, source, and name the same order. Hence a completion-facing or separated-uniform consumer receives a reflected route rather than a primitive quotient completion, selected limit, or separatedness coordinate inside the quasi-uniform carrier.
\end{proof}
