\begin{definition}[Polish-space completion-density unblock]
\label{def:polish-space-completion-density-unblock}
For an accepted $\PolishSpaceUp$ carrier
$P=(M,K,D,S,R,W,H,C,G,N)$, the completion-density unblock surface is the
finite route that exposes the $\MetricSpaceUp$ row $M$, the
$\CompleteMetricUp$ handoff $K$, and the $\SeparableMetricUp$ dense schedule
$D$ only through the shared $\StreamNameUp$ windows $S$, $\RegSeqRatUp$
readback $R$, observation ledger $W$, componentwise $\hsame$ transport $H$,
displayed $\Cont$ replay $C$, $\Pkg$ provenance $G$, and local $\NameCert$
row $N$. A downstream consumer may read complete and dense data from this
surface, but it receives no split metric carrier, selected dense point,
quotient completion equality, countable-choice schedule, or ambient
$\RealUp$ completeness datum.
\end{definition}

\begin{theorem}[Polish-space completion-density obligation]
\label{thm:polish-space-completion-density-obligation}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Every
completion-density root request first fixes the common $\MetricSpaceUp$ row
$M$, then reads the $\CompleteMetricUp$ handoff $K$ and the
$\SeparableMetricUp$ schedule $D$ through the same $\StreamNameUp$,
$\RegSeqRatUp$, and observation-ledger rows $S,R,W$. The supporting rows
$H,C,G,N$ transport, replay, source, and name only that displayed packet.
\end{theorem}
\begin{proof}
Start from \autoref{def:polish-space-completion-density-unblock}. The metric
coordinate $M$ is the single source for both the complete row $K$ and the
dense row $D$.

Read a completion-density request through $S,R,W$. The stream row supplies
the finite dense-name and Cauchy-window positions, the regular rational row
supplies the observable windows, and the ledger records that both kinds of
request use the same route.

It remains to transport and name the packet. Componentwise $\hsame$ transport
in $H$ keeps $M,K,D,S,R,W$ together, while $C,G,N$ replay, source, and name
the same finite data. No row remains from which a consumer could extract a
split metric carrier, selected dense point, quotient completion equality, or
ambient completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.PolishspaceUp.PolishSpaceCompletionDensityObligation}

\begin{theorem}[Polish-space countable dense readback]
\label{thm:polish-space-countable-dense-readback}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. Every
countable dense readback of $P$ is the finite route
$$
M \longmapsto D \longmapsto (S,R,W) \longmapsto (H,C,G,N),
$$
with any completion-facing use of $K$ read over the same $M,S,R,W$ surface.
Thus the dense readback is a displayed StreamName and RegSeqRat schedule, not
a selected dense subset, host enumeration, quotient point equality, or
countable-choice row.
\end{theorem}
\begin{proof}
Project the completion-density unblock surface. The dense schedule is the
$D$ row, and its only observation route is through the stream windows $S$,
regular rational readback $R$, and ledger $W$.

Use \autoref{thm:polish-space-completion-density-obligation}. The obligation
keeps $D$ over $M$ and forces completion-facing consumers of $K$ to share the
same $S,R,W$ readback surface.

Finally attach $H,C,G,N$. These rows do not add a second dense source; they
only transport, replay, source, and name the displayed route. Hence the
countable dense readback remains finite and schedule-based.
\end{proof}
\leanchecked{BEDC.Derived.PolishspaceUp.PolishSpaceCountableDenseReadback}

\begin{theorem}[Polish-space complete-metric separable synthesis]
\label{thm:polish-space-complete-metric-separable-synthesis}
Let $P=(M,K,D,S,R,W,H,C,G,N)$ be an accepted $\PolishSpaceUp$ carrier. The
complete-metric and separable-metric data synthesize into one
complete-separable root packet exactly when both $K$ and $D$ are consumed over
the common $\MetricSpaceUp$ row $M$ and through the shared
$\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows $S,R,W,H,C,G,N$. The synthesis exports no independent
completion coordinate, selected dense sequence, host equality, or ambient
$\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with the accepted carrier and apply
\autoref{thm:polish-space-completion-density-obligation}. The complete row
$K$ and the separable row $D$ are both read over $M$ and through the same
$S,R,W$ observation surface.

Next use \autoref{thm:polish-space-countable-dense-readback}. The dense side
has already been reduced to finite StreamName and RegSeqRat readback, and the
completion-facing use of $K$ cannot bypass that surface.

The remaining rows $H,C,G,N$ assemble the synthesis. They provide
componentwise transport, displayed replay, provenance, and local naming for
the single packet, while no carrier coordinate names an independent
completion, selected dense sequence, host equality, or ambient
real-completeness principle.
\end{proof}

\begin{theorem}[Polish-space L10 sibling route]
\label{thm:polish-space-l10-sibling-route}
Every completion-density read of an accepted $\PolishSpaceUp$ carrier is routed through the sibling chapters \autoref{ch:concrete-instances-metric-namecert}, \autoref{ch:concrete-instances-completemetric-namecert}, \autoref{ch:concrete-instances-separablemetric-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The route uses the completion-density unblock surface of \autoref{def:polish-space-completion-density-unblock}, the completion-density obligation of \autoref{thm:polish-space-completion-density-obligation}, the countable dense readback of \autoref{thm:polish-space-countable-dense-readback}, and the complete-metric separable synthesis of \autoref{thm:polish-space-complete-metric-separable-synthesis}. It adds no selected dense point, quotient completion equality, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with the unblock definition. It exposes $M,K,D,S,R,W,H,C,G,N$ as the only rows available to a completion-density consumer, with $M$ supplying the common metric source.

Apply the completion-density obligation and the countable dense readback. These place the complete-metric handoff and the separable schedule over the same StreamName and RegSeqRat windows, so the route must pass through the MetricSpace, CompleteMetric, SeparableMetric, StreamName, RegSeqRat, and Real sibling chapters named in the statement.

Finally apply the complete-metric separable synthesis. The synthesis repacks those sibling reads into the single $\PolishSpaceUp$ surface through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Since no carrier coordinate names a selected dense point, quotient completion equality, countable-choice schedule, or ambient Real-completeness theorem, the sibling route adds none of those objects.
\end{proof}
