\begin{definition}[Polish-space root-unblock carrier]
\label{def:polish-space-root-unblock-carrier}
The root-unblock carrier of an accepted $\PolishSpaceUp$ packet is the finite $\BHist$ row
$$
U=(M,K,D,S,R,B,H,C,P,N)
$$
read as follows:
\begin{enumerate}
\item $M$ is the common $\MetricSpaceUp$ source row.
\item $K$ is the $\CompleteMetricUp$ handoff row over $M$.
\item $D$ is the $\SeparableMetricUp$ dense-schedule row over $M$.
\item $S$ is the $\StreamNameUp$ finite-window row for dense-name and Cauchy-window inspections.
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows.
\item $B$ is the supporting $\BHist$ observation ledger, including metric-radius requests, complete-metric requests, separable-density requests, and the finite links among them.
\item $H$ records componentwise $\hsame$ transport for $M,K,D,S,R,B$ and the local certificate rows.
\item $C$ records displayed $\Cont$ replay from each root consumer request through the same complete-separable packet.
\item $P$ is the $\Pkg$ provenance over $\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PolishSpaceUp}$ row.
\end{enumerate}
The carrier excludes selected dense points, quotient completion equality, countable choice, and ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Polish-space common metric root unblock]
\label{thm:polish-space-root-unblock-common-metric}
Let $U=(M,K,D,S,R,B,H,C,P,N)$ be a Polish-space root-unblock carrier. Every complete-separable root consumer reads the $\CompleteMetricUp$ row $K$ and the $\SeparableMetricUp$ row $D$ only over the same $\MetricSpaceUp$ row $M$, with the finite $\BHist$ ledger $B$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$ recording that common source.

Consequently the complete side cannot use a different metric carrier from the separable side, and no selected dense point, quotient completion equality, countable-choice schedule, or ambient $\RealUp$ completeness datum is exported by the root packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polish-space-root-unblock-carrier}. The complete-metric handoff $K$ and the separable schedule $D$ are both listed after the same metric source row $M$.

Use the observation ledger $B$ to read root requests. Each complete-metric request and each separable-density request is recorded with the same metric-radius surface, so a downstream consumer cannot split the two sides across different carriers.

The rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no selected dense point, quotient completion equality, countable-choice schedule, or ambient real-completeness coordinate appears in the carrier, the common metric row exhausts the root-unblock source.
\end{proof}
\leanchecked{BEDC.Derived.PolishspaceUp.PolishSpaceRootUnblockCommonMetric}

\begin{theorem}[PolishSpace complete-separable obligation surface]
\label{thm:polishspace-complete-separable-obligation-surface}
Let $U=(M,K,D,S,R,B,H,C,P,N)$ be a Polish-space root-unblock carrier. The complete-separable obligation surface is the joint read in which $M$ is the $\MetricSpaceUp$ carrier, $K$ supplies the $\CompleteMetricUp$ convergence rows over $M$, $D$ supplies the $\SeparableMetricUp$ dense enumeration rows over the same $M$, $S$ supplies finite $\StreamNameUp$ observations, $R$ supplies $\RegSeqRatUp$ regular Cauchy witnesses and the resulting $\RealUp$ seals for observed distances, and $B,H,C,P,N$ record the observation ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ transport.

Every downstream complete-separable consumer must factor through this surface before reading any Polish-space data. The surface exports no split metric carrier, no selected dense point, no quotient-completion representative, no countable-choice schedule, and no ambient real-completeness principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polish-space-root-unblock-carrier}. The metric carrier $M$, complete row $K$, separable dense row $D$, stream row $S$, regular rational row $R$, ledger $B$, transport row $H$, replay row $C$, provenance row $P$, and local name $N$ are the displayed rows.

The complete and separable sides share the same metric source. By \autoref{thm:polish-space-root-unblock-common-metric}, $K$ and $D$ cannot be consumed over different carriers.

The finite observation discipline is supplied by \autoref{thm:polish-space-root-unblock-window-discipline}. Dense-name requests, Cauchy-window requests, and metric-radius comparisons pass through $S$ and $R$, with the Real-facing distance seals read only after the regular Cauchy witnesses have been displayed.

Finally $B,H,C,P,N$ transport, replay, source, and name that single route. Since the carrier has no field for the excluded host objects, the listed rows form the complete-separable obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.PolishspaceUp.PolishspaceCompleteSeparableObligationSurface}

\begin{theorem}[PolishSpace StreamName Real dependency anchor]
\label{thm:polishspace-streamname-real-dependency-anchor}
Let $U=(M,K,D,S,R,B,H,C,P,N)$ be a Polish-space root-unblock carrier. Any root consumer that reaches a $\RealUp$-sealed distance, convergence tolerance, or dense-radius observation must first read the $\StreamNameUp$ finite observation row $S$ and the $\RegSeqRatUp$ regular Cauchy witness row $R$. The dependency then returns to the $\MetricSpaceUp$ carrier $M$, the $\CompleteMetricUp$ convergence rows $K$, and the $\SeparableMetricUp$ dense enumeration rows $D$ through the $\BHist$ ledger $B$, componentwise transport $H$, replay $C$, provenance $P$, and local $\NameCert$ row $N$.

Thus Real-facing data in a $\PolishSpaceUp$ root packet are anchored by scheduled observations and regular Cauchy witnesses, not by an external real-number oracle or host metric completion.
\end{theorem}
\begin{proof}
Expose the stream-facing fields of \autoref{def:polish-space-root-unblock-carrier}. The only row that schedules finite observations is $S$, and the only row that turns those observations into regular rational Cauchy data is $R$.

Read a Real-facing request. The request must pass through $B$, where dense-radius, Cauchy-window, and metric comparison observations are paired with their stream positions and regular rational witnesses.

The analytic rows are then reached over the same packet. The metric carrier $M$, complete convergence row $K$, and dense enumeration row $D$ are transported together by $H$ and replayed through $C$.

The provenance and naming rows $P,N$ do not add a second Real-facing source. Therefore the dependency anchor is exactly the StreamName and RegSeqRat route followed by the common metric, complete, separable, ledger, transport, replay, provenance, and NameCert rows.
\end{proof}

\begin{theorem}[PolishSpace NameCert ledger exactness]
\label{thm:polishspace-namecert-ledger-exactness}
Let $U=(M,K,D,S,R,B,H,C,P,N)$ be a Polish-space root-unblock carrier. The local $\NameCert_{\PolishSpaceUp}$ ledger transport is exact: $N$ names precisely the $\MetricSpaceUp$ carrier $M$, the $\CompleteMetricUp$ convergence rows $K$, the $\SeparableMetricUp$ dense enumeration rows $D$, the finite $\StreamNameUp$ observations $S$, the $\RegSeqRatUp$ regular Cauchy witnesses $R$, the resulting $\RealUp$ seals recorded by the observation ledger $B$, and the componentwise $\hsame$, $\Cont$, and $\Pkg$ rows $H,C,P$.

Consequently a classified replacement of $U$ preserves the same complete-separable root packet component by component and cannot introduce hidden quotient equality, selected dense names, unrecorded limits, external real seals, or additional NameCert obligations.
\end{theorem}
\begin{proof}
Project the carrier. The local name $N$ appears only after the metric, complete, separable, stream, regular rational, ledger, transport, replay, and provenance rows have been displayed.

Use \autoref{thm:polishspace-complete-separable-obligation-surface}. It identifies the exact complete-separable surface consumed by downstream root readers, including the Real-facing seals recorded by $B$ after $S$ and $R$ have supplied finite observations and regular Cauchy witnesses.

Now transport the packet componentwise. The row $H$ compares each displayed coordinate with its replacement, $C$ replays the same requests, and $P$ preserves the stated provenance.

Since no other field remains in the root-unblock carrier, $N$ cannot name an additional obligation. The NameCert ledger transport is therefore exact for the listed rows and excludes the hidden host data named in the statement.
\end{proof}

\begin{theorem}[Polish-space window-discipline root unblock]
\label{thm:polish-space-root-unblock-window-discipline}
Let $U=(M,K,D,S,R,B,H,C,P,N)$ be a Polish-space root-unblock carrier. Every root read of dense-name coverage, Cauchy-window completion data, or metric-radius comparison factors through the $\StreamNameUp$ row $S$ and the $\RegSeqRatUp$ row $R$ before it is consumed by $M,K,D$. The supporting $\BHist$ row $B$ records exactly those windows and readbacks, while $H,C,P,N$ preserve the same route for downstream complete-separable consumers.

Thus a Polish-space root consumer receives finite window discipline over one complete-separable packet, not an unscheduled name oracle, selected dense sequence, quotient completion equality, countable-choice row, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start from the carrier. The only scheduling coordinate is $S$, and the only regular rational readback coordinate attached to it is $R$.

Read a dense-name, Cauchy-window, or metric-radius request through $B$. By definition of the root-unblock carrier, $B$ records those requests only together with the finite stream positions and regular rational observations supplied by $S$ and $R$.

It remains to route the analytic rows. The complete row $K$ and separable row $D$ are consumed only after the window and readback rows have been displayed, and the common metric row $M$ is the metric source for both.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no unscheduled oracle, selected dense sequence, quotient equality, choice row, or ambient completeness coordinate, every root read respects the displayed window discipline.
\end{proof}

\begin{definition}[Polish-space root Cauchy-basis carrier]
\label{def:polishspace-root-cauchy-basis-carrier}
The root Cauchy-basis carrier of an accepted $\PolishSpaceUp$ packet is the finite $\BHist$ row
$$
W=(M,K,D,S,R,B,A,H,C,P,N)
$$
where $M,K,D,S,R,B,H,C,P,N$ have the meanings of \autoref{def:polish-space-root-unblock-carrier}, and $A$ is the finite Cauchy-basis alignment row binding the complete-metric row $K$ and the separable dense-schedule row $D$ over the same $\MetricSpaceUp$ source, the same $\StreamNameUp$ finite-window schedule, and the same $\RegSeqRatUp$ readback data.

The alignment row records only the scheduled dense Cauchy basis seen by the local packet. It does not choose dense points, identify quotient-completion representatives, add a countable-choice schedule, or assert ambient $\RealUp$ completeness outside the displayed readback seals.
\end{definition}

\begin{theorem}[PolishSpace root Cauchy-basis obligations]
\label{thm:polishspace-root-cauchy-basis-obligations}
Let $W=(M,K,D,S,R,B,A,H,C,P,N)$ be a Polish-space root Cauchy-basis carrier. The local $\NameCert_{\PolishSpaceUp}$ surface consists exactly of common metric admission through $M$, complete-metric handoff through $K$, separable-density handoff through $D$, $\StreamNameUp$ window discipline through $S$, $\RegSeqRatUp$ readback through $R$, Cauchy-basis alignment through $A$, observation ledger support through $B$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.

No local obligation exports a selected dense point, quotient-completion equality, countable-choice schedule, ambient $\RealUp$ completeness principle, or second metric carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polishspace-root-cauchy-basis-carrier}. The rows $M,K,D,S,R,B,A,H,C,P,N$ are displayed as finite coordinates, with $A$ placed after the stream and regular-rational readback rows that make the dense Cauchy basis observable.

The common metric admission is inherited from \autoref{thm:polish-space-root-unblock-common-metric}. Both the complete-metric row $K$ and the separable-density row $D$ are read only over $M$.

The finite observation discipline is inherited from \autoref{thm:polish-space-root-unblock-window-discipline}. Dense-name coverage, Cauchy-window data, and metric-radius comparisons pass through $S$ and $R$ before reaching $K$ or $D$.

It remains to account for the Cauchy-basis row. By definition, $A$ binds the complete and separable reads to the same scheduled dense Cauchy basis over $M,S,R$; it adds no selected point or quotient representative. The rows $B,H,C,P,N$ then record the ledger, transport, replay, provenance, and local name for exactly that displayed packet.
\end{proof}

\begin{theorem}[PolishSpace completion-separability handoff]
\label{thm:polishspace-root-completion-separability-handoff}
Let $W=(M,K,D,S,R,B,A,H,C,P,N)$ be a Polish-space root Cauchy-basis carrier. Any completion-facing consumer or separability-facing consumer must factor through the single route
$$
M \longmapsto S \longmapsto R \longmapsto A \longmapsto K,D
$$
before it is used as a $\PolishSpaceUp$ root read. The rows $B,H,C,P,N$ then record the same observation ledger, componentwise transport, replay, provenance, and local naming for that route.

Consequently the completion and separability faces cannot be consumed as independent host facts; they meet only through the scheduled dense Cauchy basis aligned by $A$.
\end{theorem}
\begin{proof}
Start with a completion-facing request. The request has to read the metric source $M$, then the finite stream schedule $S$ and regular-rational readback $R$ that expose the Cauchy-window observations used by the complete row.

Now read a separability-facing request. Its dense-name coverage uses the same $M,S,R$ route, since \autoref{def:polishspace-root-cauchy-basis-carrier} gives only one stream row and one readback row for the root packet.

The alignment row $A$ is therefore the unique meeting point before $K$ and $D$ can be consumed together. It binds the complete-metric row and the separable dense-schedule row to the scheduled dense Cauchy basis, while $B,H,C,P,N$ preserve that route for downstream root reads.

Because no selected dense point, quotient-completion equality, choice schedule, or ambient completeness coordinate is present in the carrier, the displayed route is the only completion-separability handoff exported by the packet.
\end{proof}

\begin{theorem}[PolishSpace root basis-window exactness]
\label{thm:polishspace-root-basis-window-exactness}
Let $W=(M,K,D,S,R,B,A,H,C,P,N)$ be a Polish-space root Cauchy-basis carrier. The alignment row $A$ is exact only relative to the shared $\MetricSpaceUp$ row $M$, the $\StreamNameUp$ finite-window row $S$, and the $\RegSeqRatUp$ readback row $R$. A complete row $K$ and a separable row $D$ are accepted by the root packet only through that same scheduled basis window; they cannot be consumed through a different dense schedule, a host choice of dense points, a quotient-completion representative, or a second metric carrier.

Thus the basis row records a finite BEDC alignment over $M,S,R$, not an ambient assertion that completeness and separability may be read independently.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polishspace-root-cauchy-basis-carrier}. The row $A$ is listed precisely as the finite Cauchy-basis alignment binding the complete-metric row $K$ and the separable dense-schedule row $D$ over the same metric source, stream schedule, and regular-rational readback data.

Use \autoref{thm:polish-space-root-unblock-window-discipline}. Every dense-name, Cauchy-window, or metric-radius read must pass through $S$ and $R$ before it can be consumed by $M,K,D$, so a second dense schedule has no carrier coordinate.

Now apply \autoref{thm:polishspace-root-completion-separability-handoff}. The complete and separable faces meet only along the route $M \longmapsto S \longmapsto R \longmapsto A \longmapsto K,D$.

The remaining rows $B,H,C,P,N$ preserve that route as observation ledger, transport, replay, provenance, and local naming. Since the carrier has no field for host-selected dense points, quotient representatives, or another metric source, $A$ is exact only over the displayed $M,S,R$ window.
\end{proof}
