\begin{theorem}[TopGroupUp inverse Cont ledger soundness]
\label{thm:topgroup-inverse-cont-ledger-soundness}
For an accepted $\TopGroupUp$ packet, the inverse-neighbourhood continuity row
is sound exactly when its input endpoint, inverse endpoint, target
neighbourhood row, componentwise $\hsame$ transports, and finite $\Cont$ ledger
entry are all projected from the shared packet of
\autoref{def:topgroup-bhist-carrier}. The row has no additional topology carrier,
group inverse source, or external continuity predicate.
\end{theorem}
\begin{proof}
For soundness, unpack the shared packet using
\autoref{thm:topgroup-source-fiber-product-carrier}. The projected rows include
the group source, topology source, inverse graph, target neighbourhood row,
endpoint $\hsame$ transports, and the finite $\Cont$ ledger.

Apply \autoref{thm:topgroup-inverse-neighbourhood-transport}. The input endpoint
and inverse endpoint move componentwise along the displayed $\hsame$ rows, while
the topology source carries the target neighbourhood and the ledger records the
continuity step.

For the converse direction, start from an accepted public inverse-continuity
row. By \autoref{thm:topgroup-continuity-ledger-coverage}, every such row is one
of the inverse-neighbourhood entries in the same finite $\Cont$ ledger.

Apply \autoref{thm:topgroup-public-consumer-minimality}. Since the consumer
surface exposes only the displayed source certificates, inverse graph, endpoint
transports, finite ledger, and provenance row, the inverse-continuity row is
sound exactly through those packet projections and no outside datum is present.
\end{proof}

\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_inverse\_cont\_ledger\_soundness}

\begin{theorem}[TopGroupUp source compatibility obligation]
\label{thm:topgroup-source-compatibility-obligation}
Every accepted $\TopGroupUp$ root surface reads its displayed $\GroupUp$ and
$\TopologyUp$ source rows from the same $\mathsf{BHist}$ carrier, the same
carrier-aware $\hsame$ endpoint classifier, and the same $\Pkg$ provenance
packet of \autoref{def:topgroup-bhist-carrier}.
\end{theorem}
\begin{proof}
Apply \autoref{thm:topgroup-source-fiber-product-carrier}. It projects the
group source, topology source, product graph, inverse graph, neighbourhood row,
endpoint transports, finite continuity ledger, and provenance row from one
shared carrier packet.

Use \autoref{thm:topgroup-public-consumer-minimality} to read this packet from
the public side. A downstream consumer sees only the displayed source
certificates, $\hsame$ transports, finite $\Cont$ ledger, and $\Pkg$ provenance,
so the two source rows cannot be separated into different carriers.
\end{proof}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_source\_compatibility\_obligation}

\begin{theorem}[TopGroupUp operation continuity obligation]
\label{thm:topgroup-operation-continuity-obligation}
For an accepted $\TopGroupUp$ root surface, the operation-continuity obligations
exported by the carrier are exactly multiplication continuity and inversion
continuity. They are the rows covered by the product and inverse
neighbourhood-transport theorems, and no further operation-continuity row is
exported by \autoref{def:topgroup-bhist-carrier}.
\end{theorem}
\begin{proof}
First apply \autoref{thm:topgroup-product-cont-ledger-soundness}. It identifies
the multiplication-continuity row with the product graph, target neighbourhood,
endpoint $\hsame$ transports, and finite $\Cont$ ledger entry projected from
the shared carrier.

Next apply \autoref{thm:topgroup-inverse-cont-ledger-soundness}. It identifies
the inversion-continuity row with the inverse graph, target neighbourhood,
endpoint $\hsame$ transports, and its own finite $\Cont$ ledger entry.

Finally use \autoref{thm:topgroup-public-consumer-minimality}. Since the public
surface exposes only these operation rows together with the source
certificates, classifier transports, ledger, and provenance packet, there is no
third operation-continuity obligation available to a consumer.
\end{proof}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_operation\_continuity\_witness\_obligation}

\begin{theorem}[TopGroupUp continuity ledger exactness obligation]
\label{thm:topgroup-ledger-exactness-obligation}
The finite $\Cont$ ledger of an accepted $\TopGroupUp$ root surface exhausts the
continuity obligations for product and inverse rows: every accepted
product-neighbourhood or inverse-neighbourhood continuity read is one of those
two ledger families, and each listed ledger entry is sound through the shared
$\mathsf{BHist}$ packet.
\end{theorem}
\begin{proof}
Start with \autoref{thm:topgroup-continuity-ledger-coverage}. It states that
the public continuity surface is covered by the finite ledger entries for
product and inverse neighbourhood rows.

For soundness of the product entries, apply
\autoref{thm:topgroup-product-cont-ledger-soundness}; for soundness of the
inverse entries, apply \autoref{thm:topgroup-inverse-cont-ledger-soundness}.
Both proofs project the relevant endpoints, neighbourhoods, $\hsame$ transports,
and ledger rows from the same carrier packet.

Then use \autoref{thm:topgroup-public-consumer-minimality} to exclude ambient
continuity predicates or unstated operation rows. The finite $\Cont$ ledger is
therefore exact for the product and inverse continuity obligations exported by
$\TopGroupUp$.
\end{proof}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_ledger\_exactness\_obligation}

\begin{theorem}[TopGroupUp source-pair carrier obligation]
\label{thm:topgroup-source-pair-carrier-obligation}
Every accepted $\TopGroupUp$ root surface binds its $\GroupUp$ source row and
its $\TopologyUp$ source row to the same $\mathsf{BHist}$ carrier of
\autoref{def:topgroup-bhist-carrier}. The root obligation is therefore a
source-pair obligation over one carried packet, not a pair of unrelated carrier
certificates.
\end{theorem}
\begin{proof}
Apply \autoref{thm:topgroup-source-fiber-product-carrier}. It identifies the
group and topology certificates as projections from the shared packet of
\autoref{def:topgroup-bhist-carrier}.

The same theorem also records that product, inverse, neighbourhood, ledger, and
provenance rows are packet projections. Hence a root consumer can read both
source rows only through the common $\mathsf{BHist}$ carrier.
\end{proof}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_source\_pair\_carrier\_obligation}

\begin{theorem}[TopGroupUp product continuity obligation]
\label{thm:topgroup-product-continuity-obligation}
For an accepted $\TopGroupUp$ root surface, product continuity is exactly the
endpoint transport supplied by the packet's $\hsame$ rows together with the
finite $\Cont$ ledger entry for multiplication. No extra product-continuity
predicate is present outside the carrier of \autoref{def:topgroup-bhist-carrier}.
\end{theorem}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_product\_continuity\_obligation}
\begin{proof}
First use \autoref{thm:topgroup-source-fiber-product-carrier} to place the
product graph, neighbourhood row, endpoint transports, and finite ledger over
the shared source-pair carrier.

Then apply \autoref{thm:topgroup-product-cont-ledger-soundness}. Its two
directions say that a product-continuity row is sound exactly when it is this
packet projection through the $\hsame$ endpoints and the finite $\Cont$ ledger.
\end{proof}

\begin{theorem}[TopGroupUp inverse continuity obligation]
\label{thm:topgroup-inverse-continuity-obligation}
For an accepted $\TopGroupUp$ root surface, inverse continuity is the unary
endpoint-transport row carried by the packet's $\hsame$ data and the finite
$\Cont$ ledger entry for inversion. The obligation has no separate inverse
carrier, topology source, or ambient continuity witness.
\end{theorem}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_inverse\_continuity\_obligation}
\begin{proof}
Apply \autoref{thm:topgroup-source-pair-carrier-obligation} to bind the unary
inverse row to the same $\mathsf{BHist}$ carrier as the group and topology source
certificates.

Now use \autoref{thm:topgroup-inverse-cont-ledger-soundness}. It states that the
accepted inverse-continuity row is sound precisely through the input endpoint,
inverse endpoint, target neighbourhood, $\hsame$ transports, and finite
$\Cont$ ledger entry projected from that packet.
\end{proof}

\begin{theorem}[TopGroupUp operation ledger obligation]
\label{thm:topgroup-operation-ledger-obligation}
The multiplication and inverse continuity obligations of a $\TopGroupUp$
certificate are exactly the two operation-continuity ledger families supplied
by the finite $\Cont$ ledger: product-neighbourhood transport and
inverse-neighbourhood transport. There is no third operation row in the public
certificate boundary.
\end{theorem}
\begin{proof}
Use \autoref{thm:topgroup-continuity-ledger-coverage}. Every public continuity
row over the accepted packet is covered by the finite $\Cont$ ledger and is one
of the product or inverse neighbourhood transport rows.

\autoref{thm:topgroup-cont-ledger-operation-exhaustion} identifies those two
families with the product and inverse components of
\autoref{def:topgroup-bhist-continuity-obligation-triple}. It also excludes
ambient continuity predicates and any operation outside the carried product and
inverse graphs.

Finally apply \autoref{thm:topgroup-product-inverse-obligation-triad}. The
public operation surface repacks the same two continuity families with the
shared carrier compatibility row. Therefore the operation ledger obligation has
exactly two operation families and no third operation row.
\end{proof}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_operation\_ledger\_consumer\_boundary}

\begin{theorem}[TopGroupUp fixed left-translation continuity row]
\label{thm:topgroup-fixed-left-translation-continuity-row}
For an accepted $\TopGroupUp$ packet and a carried group endpoint $g$ in its
source-fiber product, the row $L_g$ defined on carried endpoints by the displayed
product graph,
$$
L_g(h)=z \quad \text{exactly when the packet displays } m(g,h,z),
$$
is a sound continuity row through the same product graph, target neighbourhood
row, componentwise $\hsame$ transports, and finite $\Cont$ ledger entry used for
multiplication. The fixed endpoint $g$ does not create a separate unary operation
source, a separate topology carrier, or an external translation-continuity
predicate.
\end{theorem}
\leanchecked{BEDC.Derived.TopGroupUp.TopGroupRootThresholdPackage\_fixed\_left\_translation\_continuity\_row}
\begin{proof}
Unpack the accepted packet by
\autoref{thm:topgroup-source-fiber-product-carrier}. The shared carrier supplies
the displayed $\NameCert_{\GroupUp}$ source row, the displayed
$\NameCert_{\TopologyUp}$ source row, the product graph $m$, the neighbourhood
row, the componentwise $\hsame$ classifier rows, the finite $\Cont$ ledger, and
the $\Pkg$ provenance row.

Fix a carried group endpoint $g$. For a carried endpoint $h$ and a displayed
product endpoint $z$ with $m(g,h,z)$, regard the left-translation read $L_g(h)=z$
as the product-neighbourhood row whose first input has been fixed to the carried
endpoint $g$. This specialization keeps the same product graph and the same
target neighbourhood row; it merely restricts the two-input product read to the
fiber over $g$.

Apply \autoref{thm:topgroup-product-neighbourhood-transport} to the product row
$m(g,h,z)$. The fixed endpoint $g$, the variable endpoint $h$, and the product
endpoint $z$ are transported only by the displayed componentwise $\hsame$ rows.
The target neighbourhood is transported inside the displayed topology source,
and the continuity step is recorded in the finite $\Cont$ ledger already carried
by the packet.

Now apply \autoref{thm:topgroup-product-cont-ledger-soundness}. It identifies
soundness of the product-continuity row exactly with the packet projections just
listed: the input endpoints, product endpoint, target neighbourhood,
componentwise $\hsame$ transports, and finite ledger entry. Since the
left-translation row is this product row with the first input fixed to $g$, its
continuity soundness is inherited from the same ledger entry and no additional
operation source is introduced.

For exhaustiveness, use \autoref{thm:topgroup-continuity-ledger-coverage}. Every
accepted product-neighbourhood continuity read is already one of the product
entries in the finite ledger. Finally,
\autoref{thm:topgroup-public-consumer-minimality} rules out any ambient
translation predicate or detached topological-group carrier. Hence the fixed
left-translation row is sound exactly through the displayed product graph,
target neighbourhood, $\hsame$ transports, and finite $\Cont$ ledger of the
accepted $\TopGroupUp$ packet.
\end{proof}
