\begin{theorem}[CauchyLimitSeal consumer readback]
\label{thm:cauchy-limit-seal-consumer-readback}
A downstream $\RealUp$ or completion consumer reads back exactly the sealed route assembled by the root-unblock package, together with the tail-extraction row of \autoref{thm:cauchy-limit-seal-tail-extraction} and the uniqueness boundary of \autoref{thm:cauchy-limit-seal-uniqueness-boundary}. The readback exports only the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Apply the root-unblock package of \autoref{thm:cauchy-limit-seal-root-unblock-package}. It gives the consumer one route from the accepted seal packet to the downstream $\RealUp$ or completion boundary.

Attach tail extraction. The tail row is already projected from the same displayed regular family, schedule, observation ledger, completion diagonal, and transport ledger, so it does not add a second consumer route.

Finally attach the uniqueness boundary. Equality-facing reads remain on the null-sequence and tail-comparison route admitted by the packet, and the readback has no coordinate for quotient completion, host uniqueness, selected limits, hidden family limits, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyLimitSeal RegSeqRat StreamName route lock]
\label{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}
Every accepted $\CauchyLimitSealUp$ packet consumed by a $\RealUp$ or completion-facing route factors through the displayed $\StreamNameUp$ finite window of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the $\RealUp$ seal row of \autoref{ch:concrete-instances-real-namecert}, and the $\RealCauchyCompletionUp$ consumer boundary of \autoref{ch:concrete-instances-real-cauchy-completion-namecert}. The factorization uses only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already exposed by the accepted seal route.

Consequently the accepted consumer route exports no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completion row, or standard bridge row outside that finite L10 route.
\end{theorem}
\begin{proof}
Start with the consumer readback theorem, \autoref{thm:cauchy-limit-seal-consumer-readback}. It confines every downstream $\RealUp$ or completion consumer to the accepted seal packet, its root-unblock route, tail-extraction row, uniqueness boundary, and the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, and $\RealUp$ rows.

Next attach the finite route theorems already exposed on the Real side. The four-face canonical route of \autoref{thm:real-l10-four-face-canonical-route} and the seal lattice of \autoref{thm:real-streamname-regseqrat-seal-lattice} force any completion-facing $\RealUp$ consumer carrying a $\CauchyLimitSealUp$ row through the ordered $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces before the seal row is read.

Finally use the terminal comparison exhaustion of \autoref{thm:real-l10-terminal-comparison-exhaustion} together with the $\RealCauchyCompletionUp$ consumer boundary cited above. These rows keep the completion-facing endpoint on the same displayed histories, transports, continuations, provenance, and local names, so no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completion coordinate, or standard bridge coordinate remains available to the consumer.
\end{proof}

\begin{theorem}[Real-completion seal selector consumer factorization]
\label{thm:real-completion-seal-selector-consumer-factorization}
Let an accepted $\CauchyLimitSealUp$ consumer be routed through an accepted $\RealCompletionSelectorSealUp$ packet and an accepted $\ObserverFilterBudgetSelectorUp$ budget packet for the current Real and Completion handoff. Then its consumer read factors through the concrete displayed chain
$$
\ObserverFilterBudgetSelectorUp \to \StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \CauchyLimitSealUp \to \RealUp.
$$
The factorization uses only the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the three accepted packets. It exports no quotient stream, host real equality, hidden selector, detached limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with the route lock of \autoref{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}. It confines the $\CauchyLimitSealUp$ consumer to the displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ rows, with only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Next attach the selector-seal packet. The L10 handoff scope of \autoref{thm:real-completion-selector-seal-l10-handoff-scope} identifies the selector-seal consumer as the same finite route through selector budget, selected window, regular readback, limit-seal handoff, and terminal $\RealUp$ endpoint.

Finally attach the observer-budget packet. The bridge-ready route of \autoref{thm:observer-filter-budget-selector-bridge-ready-route} supplies the selected observer row, finite budget, selected $\StreamNameUp$ window, dyadic ledger, regular handoff, and Real seal in that order. Combining the three displayed routes gives the stated factorization, and the coordinate exclusions in the cited theorems leave no quotient stream, host real equality, hidden selector, detached limit, or ambient completeness row for the consumer.
\end{proof}

\begin{theorem}[CauchyLimitSeal finite-request section compatibility]
\label{thm:cauchy-limit-seal-finite-request-section-compatibility}
Let $P$ be an accepted $\CauchyLimitSealUp$ packet whose public route is consumed by a finite request section $S$ for the current Real and Completion handoff. Then the accepted consumer boundary is the same finite $\BHist$ packet whether it is read through the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ readback section, the $\DyadicRatCoreUp$ endpoint and radius ledger, the local $\RealUp$ seal row, or the $\CauchyLimitSealUp$ public route packet:
$$
S_{\StreamNameUp}=S_{\RegSeqRatUp}=S_{\DyadicRatCoreUp}=S_{\RealUp}=S_{\CauchyLimitSealUp}
$$
as displayed finite $\BHist$ sections over the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The compatibility exports no quotient stream equality, host real equality, selected limit, countable-choice schedule, ambient completeness principle, metric-completion row, or standard bridge row.
\end{theorem}
\begin{proof}
Start with the route lock of \autoref{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}. It confines the accepted $\CauchyLimitSealUp$ consumer to the displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ rows, so every face of $S$ is read from the same public route packet.

Next read the Real-facing side through \autoref{thm:real-regseqrat-finite-request-fusion} and \autoref{thm:real-regseqrat-finite-request-section-terminality}. These theorems identify the $\RealUp$ seal request with one finite $\BHist$ packet carrying the StreamName window, dyadic endpoint-radius ledger, RegSeqRat classifier and readback rows, componentwise $\hsame$ transport, displayed $\Cont$ route, $\mathsf{Pkg}$ provenance, and local $\NameCert_{\RealUp}$ row.

Now read the StreamName-facing side through \autoref{thm:streamname-finite-request-section-pullback} and \autoref{thm:streamname-finite-section-pullback-exactness}. The pullback section has the same finite window face and the same dyadic, RegSeqRat, and Real seal faces, so it cannot introduce a second selector or a second completion-facing section.

Finally apply the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape}. Since the accepted packet has no coordinate for quotient stream equality, host real equality, selected limits, countable-choice schedules, ambient completeness, metric-completion rows, or standard bridge rows, the only consumer boundary left is the displayed finite $\BHist$ packet shared by all five readings.
\end{proof}

\begin{theorem}[CauchyLimitSeal downstream consumer coverage]
\label{thm:cauchy-limit-seal-downstream-consumer-coverage}
Let an accepted local $\CauchyLimitSealUp$ consumer be read by a downstream $\RealUp$ or completion-facing consumer through the selected $\RealCompletionSelectorSealUp$ and $\ObserverFilterBudgetSelectorUp$ packets of the current handoff. Then the consumer read is exhausted by the displayed finite route rows
$$
\ObserverFilterBudgetSelectorUp \to \StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \CauchyLimitSealUp \to \RealUp,
$$
together with the $\RealCauchyCompletionUp$ consumer boundary, the tail-extraction row, the uniqueness boundary, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already named in the selected packet.

Equivalently, every accepted use of the local consumer is one of the listed selected observer, finite budget, finite window, dyadic ledger, regular readback, limit-seal handoff, terminal Real endpoint, completion-boundary, tail, comparison, transport, replay, provenance, or naming rows. A purported quotient stream, host sequence equality, host real equality, hidden selector, detached limit, selected host limit, hidden family limit, ambient completeness principle, metric-completion row, standard bridge row, arithmetic package, or order package is outside the displayed BEDC packet and is not exported by the consumer readback.
\end{theorem}
\begin{proof}
Start with the consumer factorization of \autoref{thm:real-completion-seal-selector-consumer-factorization}. It places any accepted local $\CauchyLimitSealUp$ consumer that enters through the selected selector-seal and observer-budget packets on the concrete route
$$
\ObserverFilterBudgetSelectorUp \to \StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \CauchyLimitSealUp \to \RealUp.
$$
The same theorem records that the route uses only the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the accepted packets, and that quotient streams, host real equality, hidden selectors, detached limits, and ambient completeness have no exported coordinate there.

Now apply the route lock of \autoref{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}. It places the local $\CauchyLimitSealUp$ portion of the same read on the displayed $\StreamNameUp$ finite window, $\RegSeqRatUp$ readback surface, $\DyadicRatCoreUp$ tolerance ledger, $\RealUp$ seal row, and $\RealCauchyCompletionUp$ consumer boundary, with the componentwise transport row supplied by \autoref{thm:cauchy-limit-seal-public-route-transport}. Thus the selector route cannot open a second local consumer surface; it can only read the same finite window, ledger, readback, seal, and completion-boundary rows.

The remaining local readback rows are already fixed by \autoref{thm:cauchy-limit-seal-consumer-readback}. Tail-facing use is projected by \autoref{thm:cauchy-limit-seal-tail-extraction}, and equality-facing use is confined by \autoref{thm:cauchy-limit-seal-uniqueness-boundary}. The transport component for those tail and comparison rows is the packet-local public route transport of \autoref{thm:cauchy-limit-seal-public-route-transport}. These two rows account for the admitted tail and comparison alternatives without adding quotient completion, host uniqueness, selected limits, hidden family limits, or ambient completeness.

Combining the factorized selector route with the locked local route and the readback tail and comparison rows along the public-route transport of \autoref{thm:cauchy-limit-seal-public-route-transport} gives the announced coverage list. Any purported downstream coordinate not on that list would have to bypass either the displayed selector chain, the locked $\StreamNameUp$--$\RegSeqRatUp$--$\DyadicRatCoreUp$--$\RealUp$--$\RealCauchyCompletionUp$ surface, or the packet-local tail and uniqueness rows. Each bypass is excluded by the cited theorems, so the unlisted alternatives remain outside the BEDC packet and cannot be exported by the consumer readback.
\end{proof}
