\section{CauchyLimitSeal regular tail-selector sibling link}
\label{sec:cauchy-limit-seal-regular-tail-selector-sibling-link}

\begin{theorem}[CauchyLimitSeal regular tail-selector sibling link]
\label{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}
Every accepted $\CauchyLimitSealUp$ seal route whose selector and observation-budget reads use the transport surface of \autoref{thm:cauchy-limit-seal-selector-budget-transport} factors first through the accepted $\RegularCauchyTailSelectorUp$ packet of \autoref{ch:concrete-instances-regularcauchytailselector-namecert}. The route reaches the shared $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, and $\RealObservationBudgetUp$ meet only after the regular tail-selector packet has supplied its selected-tail witness and its finite support rows. Consequently the seal route exports no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_regular\_tail\_selector\_sibling\_link}
\begin{proof}
Begin with the regular tail-selector packet. The consumer package of \autoref{thm:regular-cauchy-tail-selector-diagonal-consumer-package} supplies one finite selected-tail witness together with the requested precision, $\StreamNameUp$ window, $\RegSeqRatUp$ regularity row, $\DyadicRatCoreUp$ comparison row, componentwise $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row.

Now attach the seal-side meet. By \autoref{thm:cauchy-limit-seal-tail-budget-meet}, the $\CauchyLimitSealUp$ route and the $\RealObservationBudgetUp$ route share one finite meet over the same regular handoff, window, dyadic ledger, Real seal, transport, continuation, provenance, and naming rows.

Finally use selector-budget transport from \autoref{thm:cauchy-limit-seal-selector-budget-transport}. It preserves the selector read, budget read, and completion-facing read along the same displayed route, so those reads cannot pass around the accepted $\RegularCauchyTailSelectorUp$ packet before consuming the shared window, ledger, handoff, seal, and meet rows.

The non-escape clauses of the cited selector package and meet route exclude quotient stream identity, host real equality, choice-selected limits, hidden family limits, and ambient completeness. The sibling link is therefore a finite factorization through the displayed regular tail-selector packet rather than an additional completion principle.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular tail-selector budget compatibility]
\label{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}
Every selector-budget read compatible with \autoref{thm:cauchy-limit-seal-selector-budget-transport} factors through the same accepted $\RegularCauchyTailSelectorUp$ packet before it reaches the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, and $\RealObservationBudgetUp$ rows. Thus the selector route, observation-budget route, and completion-facing route share one finite tail-selector factorization.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_regular\_tail\_selector\_budget\_compatibility}
\begin{proof}
Begin with the sibling-link theorem \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. It places every compatible seal route through the accepted regular tail-selector packet before the stream, dyadic, regular-sequence, Real, and observation-budget rows are consumed.

Next apply selector-budget transport from \autoref{thm:cauchy-limit-seal-selector-budget-transport}. The transported selector read, budget read, and completion-facing read remain on the same precision request, finite window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and naming rows.

Finally use the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. The meet binds the seal side and observation-budget side to the same finite route, so every compatible selector-budget read inherits the regular tail-selector factorization.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular tail-selector non-escape]
\label{thm:cauchy-limit-seal-regular-tail-selector-nonescape}
After a compatible selector route is read through the accepted $\RegularCauchyTailSelectorUp$ packet, the $\CauchyLimitSealUp$ seal cannot export quotient stream identity, host real equality, a choice-selected limit, a hidden family limit, or ambient completeness. The exported boundary is only the selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_regular\_tail\_selector\_nonescape}
\begin{proof}
Start from the budget compatibility theorem above. It fixes the selector, budget, and completion-facing reads on the same regular tail-selector packet and the same tail-budget meet.

Use the selector package theorem \autoref{thm:regular-cauchy-tail-selector-diagonal-consumer-package}. Its consumer surface contains the finite selected-tail witness and support rows, with no quotient representative, equality row, infinite-tail row, or completeness coordinate.

Finally apply \autoref{thm:cauchy-limit-seal-selector-budget-transport} and \autoref{thm:cauchy-limit-seal-tail-budget-meet}. Transport preserves the finite route, and the meet adds no hidden completion coordinate. The named non-escape objects therefore cannot be exported after the selector route has been read.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-selector window support determinacy]
\label{thm:cauchy-limit-seal-tail-selector-window-support-determinacy}
Every compatible $\CauchyLimitSealUp$ route that factors through the accepted $\RegularCauchyTailSelectorUp$ packet reads the same selected-tail witness, $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, and $\RealObservationBudgetUp$ meet across the selector route, observation-budget route, and completion-facing route. Thus selector-facing, budget-facing, and completion-facing consumers share one finite support packet rather than three independent reads.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_selector\_window\_support\_determinacy}
\begin{proof}
First apply the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. It routes every compatible seal read through the accepted regular tail-selector packet before the selected-tail witness, StreamName window, DyadicRatCore ledger, RegSeqRat handoff, Real seal, and observation-budget meet are consumed.

Next use budget compatibility from \autoref{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}. The selector route, observation-budget route, and completion-facing route are all factored through the same accepted packet and the same tail-budget meet, so their support rows are not independently chosen.

Finally apply the non-escape theorem \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. Since no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate is available, the three reads cannot diverge outside the displayed finite support. Their selected-tail witness, window, ledger, handoff, seal, and meet are therefore determined by the same packet.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular tail-selector public export]
\label{thm:cauchy-limit-seal-regular-tail-selector-public-export}
Every compatible public $\CauchyLimitSealUp$ export to a Real-facing completion consumer factors through one accepted $\RegularCauchyTailSelectorUp$ packet, then through the shared $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, and $\RealObservationBudgetUp$ meet. The exported boundary is exactly this finite selector-support route and does not include quotient stream identity, host real equality, choice-selected limits, hidden family limits, or ambient completeness.
\end{theorem}
\begin{proof}
First apply the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. It places the public seal route through the accepted regular tail-selector packet before any Real-facing completion consumer can read the StreamName, DyadicRatCore, RegSeqRat, Real, or observation-budget rows.

Next use budget compatibility from \autoref{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}. The selector-facing, budget-facing, and completion-facing reads are the same finite route over the accepted packet and the tail-budget meet, so the public export cannot choose a second support surface.

Now apply the non-escape boundary of \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. It removes quotient stream identity, host real equality, choice-selected limits, hidden family limits, and ambient completeness from the export inventory.

Finally use window support determinacy from \autoref{thm:cauchy-limit-seal-tail-selector-window-support-determinacy}. The selected-tail witness, shared window, dyadic ledger, regular-sequence handoff, Real seal, and observation-budget meet are determined by the single accepted packet, so every compatible public export factors through precisely that route.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular tail-selector classifier stability]
\label{thm:cauchy-limit-seal-regular-tail-selector-classifier-stability}
Let two accepted $\CauchyLimitSealUp$ routes be related by the local classifier of the chapter. If the first route factors through the accepted $\RegularCauchyTailSelectorUp$ packet of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}, then the transported route factors through the transported regular tail-selector packet. The transported factorization preserves the selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate is exported by the classifier transport.
\end{theorem}
\begin{proof}
First apply the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link} to the source route. It gives the accepted regular tail-selector packet before the selected-tail witness, StreamName window, dyadic ledger, regular-sequence handoff, Real seal, observation-budget meet, transport, continuation, provenance, and naming rows are read.

Next use budget compatibility from \autoref{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}. The selector-facing, budget-facing, and completion-facing reads are one finite route, so the local classifier has a single support packet to transport rather than separate selector and budget witnesses.

Now apply choice-free selector stability from \autoref{thm:cauchy-limit-seal-choice-free-selector-stability}. The classifier transport preserves the admitted selector route, the finite support windows, the dyadic ledger, the displayed $\hsame$ comparisons, and the $\Cont$ replay rows. Thus the transported route lands in the transported regular tail-selector packet with the same selected-tail witness surface.

Use window support determinacy from \autoref{thm:cauchy-limit-seal-tail-selector-window-support-determinacy} to identify the transported packet's public rows. The selected-tail witness, StreamName window, DyadicRatCore ledger, RegSeqRat handoff, Real seal, and RealObservationBudget meet are the rows determined by that one packet, and the displayed $\Pkg$ and $\NameCert$ rows travel with the same classifier route.

Finally invoke the non-escape theorem \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. Since neither the source factorization nor the classifier transport contains quotient stream identity, host real equality, choice-selected limits, hidden family limits, or ambient completeness, the transported public export remains exactly the regular tail-selector factorization described above.
\end{proof}

\begin{theorem}[CauchyLimitSeal StreamName cofinal tail-budget fusion]
\label{thm:cauchy-limit-seal-streamname-cofinal-tail-budget-fusion}
Every accepted $\CauchyLimitSealUp$ route whose selector-budget transport factors through the regular tail-selector sibling and whose completion-facing read uses the tail-budget meet factors through one finite envelope. The envelope consists of the $\RegularCauchyTailSelectorUp$ selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, the $\CofinalTailBudgetUp$ shared-tail row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Consequently the fused route exports no quotient stream identity, host sequence equality, hidden tail selector, countable-choice schedule, selected host limit, independent completion row, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. It routes the accepted seal read through the regular tail-selector packet before the selected-tail witness, StreamName window, dyadic ledger, regular-sequence handoff, Real seal, transport, continuation, provenance, and naming rows are consumed.

Next use the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. The meet binds the selector-facing read, observation-budget read, and completion-facing read to the same finite route, so the completion consumer cannot choose a second row outside the selector packet.

Transport that common route by \autoref{thm:cauchy-limit-seal-selector-budget-transport}. Componentwise $\hsame$ transport and the displayed $\Cont$ replay preserve the precision request, the finite $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\BHist$ surface, the $\Pkg$ provenance, and the local $\NameCert$ row.

Now attach the cofinal shared-tail row by \autoref{thm:cofinal-tail-budget-primitive-scope-binding}. Its primitive scope is the finite shared-tail budget packet, so it adds only the public $\CofinalTailBudgetUp$ row aligned with the same regular handoff and completion-facing consumer.

Finally invoke the non-escape boundary of \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. Together with the cofinal primitive scope, it removes quotient stream identity, host sequence equality, hidden tail selectors, countable-choice schedules, selected host limits, independent completion rows, and ambient $\RealUp$ completeness from the exported route.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular tail-selector ProbeBundle coverage]
\label{thm:cauchy-limit-seal-regular-tail-selector-probebundle-coverage}
Let $Q$ be an accepted $\CauchyLimitSealUp$ route compatible with the regular tail-selector sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. Every finite $\mathsf{ProbeBundle}$ of selector-facing, observation-budget-facing, and completion-facing requests for $Q$ factors through one finite envelope. The envelope consists of the $\RegularCauchyTailSelectorUp$ selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, the $\CofinalTailBudgetUp$ shared-tail row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Thus finite bundled consumers receive the same route-level support as the pointwise fused route. The bundle exposes no quotient stream identity, host sequence equality, hidden selector, countable-choice schedule, selected host limit, independent completion row, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Induct over the finite $\mathsf{ProbeBundle}$. The empty bundle uses the finite envelope already displayed by the accepted route, with no consumer request to place outside it.

For a successor request, apply the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link} and budget compatibility from \autoref{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}. The new selector-facing, observation-budget-facing, or completion-facing read is forced through the accepted regular tail-selector packet before it can read the StreamName window, dyadic ledger, regular-sequence handoff, Real seal, observation-budget meet, transport, continuation, package, or naming rows.

Next use the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet} and selector-budget transport from \autoref{thm:cauchy-limit-seal-selector-budget-transport}. These identify the support of the new request with the accumulated support of the earlier bundle entries, so the induction step does not introduce a second budget row or a second selector packet.

Now attach the cofinal shared-tail row by the fusion theorem \autoref{thm:cauchy-limit-seal-streamname-cofinal-tail-budget-fusion}. It places the $\CofinalTailBudgetUp$ coordinate on the same StreamName, DyadicRatCore, RegSeqRat, Real, observation-budget, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already carried by the bundle envelope.

Finally apply the non-escape theorem \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. Since neither the pointwise route nor the finite induction step can export quotient stream identity, host sequence equality, hidden selectors, countable-choice schedules, selected host limits, independent completion rows, or ambient $\RealUp$ completeness, the finite bundle repacks as one $\mathsf{ProbeBundle}$ coverage row over exactly the displayed envelope.
\end{proof}

\begin{theorem}[CauchyLimitSeal ProbeBundle envelope terminality]
\label{thm:cauchy-limit-seal-probebundle-envelope-terminality}
Let $Q$ be an accepted $\CauchyLimitSealUp$ route compatible with the regular tail-selector sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. Among all public factorization surfaces for finite $\mathsf{ProbeBundle}$ families of selector-facing, observation-budget-facing, and completion-facing requests for $Q$, the envelope of \autoref{thm:cauchy-limit-seal-regular-tail-selector-probebundle-coverage} is terminal. It consists of the $\RegularCauchyTailSelectorUp$ selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, the $\CofinalTailBudgetUp$ shared-tail row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Every alternative public route with the same visible reads is classifier-equal to this envelope. No quotient stream identity, host sequence equality, hidden selector, countable-choice schedule, selected host limit, independent completion row, or ambient $\RealUp$ completeness can separate a second public factorization surface from it.
\end{theorem}
\begin{proof}
Start from the sibling link of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. It places every compatible accepted route through the regular tail-selector packet before any selector-facing, observation-budget-facing, or completion-facing request can read the StreamName window, dyadic ledger, regular-sequence handoff, Real seal, continuation, package, or naming rows.

Next combine budget compatibility from \autoref{thm:cauchy-limit-seal-regular-tail-selector-budget-compatibility}, non-escape from \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}, and window-support determinacy from \autoref{thm:cauchy-limit-seal-tail-selector-window-support-determinacy}. These three results force the selector, budget, and completion reads onto one displayed support packet and rule out every hidden coordinate that could distinguish another public surface.

Now use the cofinal tail-budget fusion theorem \autoref{thm:cauchy-limit-seal-streamname-cofinal-tail-budget-fusion}. It attaches the $\CofinalTailBudgetUp$ shared-tail row to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support, so the fused route has no independent completion row outside the regular tail-selector envelope.

Finally apply the finite $\mathsf{ProbeBundle}$ induction from \autoref{thm:cauchy-limit-seal-regular-tail-selector-probebundle-coverage}. The empty bundle has only the displayed envelope. Each successor request is already forced through that envelope by the preceding compatibility and fusion steps, so adding a request cannot create a second public route. Any alternative route with the same visible reads is therefore classifier-equal to the displayed envelope, which proves terminality.
\end{proof}

\begin{corollary}[CauchyLimitSeal regular tail-selector strict local obstruction]
\label{cor:cauchy-limit-seal-regular-tail-selector-strict-local-obstruction}
Let an accepted $\CauchyLimitSealUp$ route be read through the regular tail-selector sibling surface of \autoref{thm:cauchy-limit-seal-regular-tail-selector-sibling-link}. Any displayed failure, refusal, separation, or countermodel row attached to that sibling surface obstructs only the named converse or reuse route that tries to read outside the local factorization. Its scope is the selected-tail witness, the $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegSeqRatUp$ handoff, the $\RealUp$ seal, the $\RealObservationBudgetUp$ meet, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It cannot be reinterpreted as a global impossibility for $\CauchyLimitSealUp$ packets, a host theorem about real equality or completeness, or a hidden external validation principle.
\end{corollary}
\begin{proof}
Start with the non-escape theorem \autoref{thm:cauchy-limit-seal-regular-tail-selector-nonescape}. After the compatible selector route has been read through the accepted $\RegularCauchyTailSelectorUp$ packet, the exported boundary is exactly the selected-tail witness, the stream window, the dyadic ledger, the regular-sequence handoff, the Real seal, the observation-budget meet, and the displayed transport, continuation, provenance, and naming rows. The same theorem removes quotient stream identity, host real equality, choice-selected limits, hidden family limits, and ambient completeness from the export inventory.

Now apply classifier stability from \autoref{thm:cauchy-limit-seal-regular-tail-selector-classifier-stability}. Classifier transport preserves the same finite packet and the same displayed rows. Hence any consumer-facing use of a failure, refusal, separation, or countermodel row must factor through the transported local packet before it can be read by a selector-facing, budget-facing, or completion-facing consumer.

The obstruction is therefore strict. If the blocked request is a named converse or reuse route, the block occurs exactly where that route asks for an unlisted coordinate outside the finite packet. Since the classifier transport has no coordinate beyond the listed rows, the obstruction cannot be promoted to a global impossibility for other $\CauchyLimitSealUp$ packets, cannot become a host theorem asserting real equality or completeness, and cannot certify an external validation source. It records only the failure of the named local route to pass the displayed sibling boundary.
\end{proof}
