\begin{theorem}[CauchyLimitSeal tail-budget meet]
\label{thm:cauchy-limit-seal-tail-budget-meet}
Let
$$
L=(X,S,D,G,E,T,P,N)
$$
be an accepted $\CauchyLimitSealUp$ packet, and let
$$
B=(E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\RealObservationBudgetUp$ packet over the same displayed precision request and finite $\StreamNameUp$ window. If the seal row $S_B$ and the regular handoff rows $R_B$ are routed through $L$, then there is a single finite meet row over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ that binds the selector read, the observation-budget read, and the completion-consumer read to one BEDC route. The meet row contains no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_budget\_meet}
\begin{proof}
Start with tail extraction from \autoref{thm:cauchy-limit-seal-tail-extraction}. It projects every admitted tail read of $L$ from the displayed regular family, stream schedule, dyadic observation ledger, diagonal row, seal row, and visible transport route.

Attach the $\RealObservationBudgetUp$ side using \autoref{thm:cauchy-limit-seal-real-observation-budget-consumer-package}. Since the budget packet and the seal packet share the displayed precision request and window, the budget rows and seal rows meet over the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.

Finally use budget root source totality from \autoref{thm:cauchy-limit-seal-budget-root-source-totality}. It says every accepted budget-facing read is sourced by the listed seal and budget rows, so the selector, budget, and completion reads have one finite route and no extra completion, quotient, equality, selection, hidden-family, or ambient-completeness coordinate.
\end{proof}

\begin{theorem}[CauchyLimitSeal selector-budget transport]
\label{thm:cauchy-limit-seal-selector-budget-transport}
In the setting of \autoref{thm:cauchy-limit-seal-tail-budget-meet}, componentwise $\hsame$ transport and the displayed $\Cont$ routes preserve the meet row through selector admission and observation-budget transport. Thus any transported selector read, budget read, or completion-facing read remains on the same precision request, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, $\BHist$ surface, $\Pkg$ provenance, and local $\NameCert$ row. Transport does not introduce quotient stream identity, host real equality, a choice-selected limit, a hidden family limit, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_selector\_budget\_transport}
\begin{proof}
Project the meet row supplied by \autoref{thm:cauchy-limit-seal-tail-budget-meet}. Its readable coordinates are already the selector, budget, and completion-consumer coordinates on the shared finite route.

For the selector side, use \autoref{thm:cauchy-limit-seal-choice-free-selector-stability}. It transports the admitted selector route componentwise through the displayed $\hsame$ comparisons and $\Cont$ replays while preserving the selected finite windows and dyadic ledger.

For the budget side, use the observation-budget pullback and consumer package from \autoref{thm:cauchy-limit-seal-observation-budget-pullback} and \autoref{thm:cauchy-limit-seal-real-observation-budget-consumer-package}. These rows preserve the precision request, window, ledger, regular handoff, seal, route, provenance, and naming rows. Hence every transported read remains inside the same finite meet packet.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-budget meet exactness]
\label{thm:cauchy-limit-seal-tail-budget-meet-exactness}
Let $L$ be an accepted $\CauchyLimitSealUp$ packet and let $B$ be an accepted $\RealObservationBudgetUp$ packet over the same displayed precision request and finite $\StreamNameUp$ window. The two packets classify through the same finite tail-budget meet row if and only if their selector row, observation-budget row, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows agree componentwise inside the meet surface. This exactness statement excludes quotient stream identity, host real equality, choice-selected limits, hidden family limits, and ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_budget\_meet\_exactness}
\begin{proof}
For the forward direction, project the finite meet row supplied by \autoref{thm:cauchy-limit-seal-tail-budget-meet}. The meet has no coordinates other than the selector, budget, dyadic ledger, regular handoff, real seal, transport, continuation, provenance, and naming rows, so classification through the same row identifies those coordinates componentwise.

Apply \autoref{thm:cauchy-limit-seal-selector-budget-transport}. It keeps the selector side and observation-budget side on the same precision request, stream window, dyadic ledger, regular handoff, real seal, transport row, continuation route, package row, and local name under every displayed $\hsame$ and $\Cont$ replay.

For the reverse direction, start from componentwise agreement of the listed coordinates. Repack the selector read, observation-budget read, dyadic ledger, regular handoff, real seal, transports, routes, provenance, and naming row into the meet supplied by \autoref{thm:cauchy-limit-seal-tail-budget-meet}.

The repacked meet is accepted because each coordinate is already an accepted coordinate of $L$ and $B$ over the same precision request and finite window. Since no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate is present, the shared componentwise row is exactly the common classifier surface.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular-tail budget exactness]
\label{thm:cauchy-limit-seal-regular-tail-budget-exactness}
Suppose an accepted $\CauchyLimitSealUp$ packet and an accepted $\RealObservationBudgetUp$ packet share the same finite $\StreamNameUp$ window and the same $\RegSeqRatUp$ handoff. Inside the tail-budget meet, the regular-tail budget is exact if and only if the selector row, observation-budget row, dyadic ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row agree.

The exact regular-tail budget has no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
For the forward direction, project the shared meet by \autoref{thm:cauchy-limit-seal-tail-budget-meet}. Since the two packets share the StreamName window and RegSeqRat handoff, the remaining readable budget coordinates are precisely the selector, observation-budget, dyadic-ledger, real-seal, transport, continuation, provenance, and naming rows.

Apply \autoref{thm:cauchy-limit-seal-selector-budget-transport}. It keeps the selector read and the observation-budget read on the same regular-tail route under the displayed $\hsame$ transports and $\Cont$ replays.

For the reverse direction, assume the listed rows agree componentwise. Repack those rows into the meet supplied by \autoref{thm:cauchy-limit-seal-tail-budget-meet}; the already shared StreamName window and RegSeqRat handoff give the regular-tail spine, and the agreed rows fill the budget surface.

Finally use \autoref{thm:cauchy-limit-seal-tail-budget-meet-exactness}. It identifies componentwise agreement inside the meet with classification through the same finite tail-budget row and excludes the listed quotient, host-equality, selected-limit, hidden-family, and ambient-completeness coordinates.
\end{proof}

\begin{theorem}[CauchyLimitSeal completion-budget root unblock]
\label{thm:cauchy-limit-seal-completion-budget-root-unblock}
The tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet} and its selector-budget transport of \autoref{thm:cauchy-limit-seal-selector-budget-transport} package the root-unblock and completion-consumer rows into one downstream surface. A $\RealUp$ or completion consumer may cite this surface as the finite route through $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ supplied by the accepted $\CauchyLimitSealUp$ and $\RealObservationBudgetUp$ packets. The package explicitly excludes quotient stream identity, host real equality, choice-selected limits, hidden family limits, and ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_completion\_budget\_root\_unblock}
\begin{proof}
First take the root-unblock package from \autoref{thm:cauchy-limit-seal-root-unblock-package}. It supplies the downstream route from the accepted seal packet to the Real and completion consumer boundary.

Next refine that route by the tail-budget meet. The meet binds the selector read and the observation-budget read to the same displayed precision and window route before the completion consumer reads the packet.

Finally apply \autoref{thm:cauchy-limit-seal-root-completion-consumer-nonescape}. The completion-facing endpoint can export only the rows listed by the root source and dyadic-window exactness theorems, so the combined package has no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-budget consumer normal form]
\label{thm:cauchy-limit-seal-tail-budget-consumer-normal-form}
Every $\RealUp$ or completion consumer of the tail-budget meet factors through exactly the shared precision request, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row named by \autoref{thm:cauchy-limit-seal-tail-budget-meet} and \autoref{thm:cauchy-limit-seal-selector-budget-transport}. This consumer route has no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_budget\_consumer\_normal\_form}
\begin{proof}
First cite the meet theorem \autoref{thm:cauchy-limit-seal-tail-budget-meet}. It binds the selector read, observation-budget read, and completion-consumer read to one finite route over the shared precision request, finite stream window, dyadic ledger, regular handoff, real seal, transport, continuation, provenance, and naming rows.

Next apply the selector-budget transport theorem \autoref{thm:cauchy-limit-seal-selector-budget-transport}. It keeps those rows stable under componentwise $\hsame$ transport and displayed $\Cont$ replay, so a transported selector, budget, or completion-facing read cannot leave the same finite packet.

Finally close with \autoref{thm:cauchy-limit-seal-completion-budget-root-unblock}. The root-unblock package is therefore consumed only through the displayed meet and transport route, excluding quotient stream identity, host real equality, choice-selected limit, hidden family limit, and ambient completeness.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-meet uniform selector route]
\label{thm:cauchy-limit-seal-tail-meet-uniform-selector-route}
Let
$$
L=(X,S,D,G,E,T,P,N)
$$
be an accepted $\CauchyLimitSealUp$ packet, let
$$
B=(E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B)
$$
be an accepted $\RealObservationBudgetUp$ packet over the same displayed precision request and finite $\StreamNameUp$ window, and let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted $\UniformCauchyCriterionUp$ packet whose displayed finite window, dyadic tolerance, $\RegSeqRatUp$ tail row, and $\RealUp$ seal handoff are exactly the rows read by the tail-budget meet. Then every $\RealUp$ or $\CompletionUp$ consumer using the selector-budget route factors through one finite envelope: the $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\UniformCauchyCriterionUp$ tail ledger, $\RealObservationBudgetUp$ rows, $\CauchyLimitSealUp$ seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. This route has no quotient stream, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_meet\_uniform\_selector\_route}
\begin{proof}
Begin with the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. It binds the selector read, the observation-budget read, and the completion-consumer read to the displayed precision request, finite stream window, dyadic ledger, regular handoff, real seal, transport, continuation, provenance, and naming rows.

Transport that meet by \autoref{thm:cauchy-limit-seal-selector-budget-transport}. The selector-budget route preserves the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealObservationBudgetUp$, $\CauchyLimitSealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface under every displayed replay.

Apply the consumer normal form of \autoref{thm:cauchy-limit-seal-tail-budget-consumer-normal-form}. A $\RealUp$ or $\CompletionUp$ consumer therefore receives the meet only through the stated finite envelope and cannot switch to a quotient stream, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, or ambient completeness witness.

Finally attach the UniformCauchyCriterion side by \autoref{thm:regular-cauchy-tail-meet-completion-uniform-frontier} and \autoref{thm:uniform-cauchy-criterion-finite-family-seal-obligation-package}. These frontiers force the displayed uniform tail ledger to read the same finite family, dyadic tolerance, regular-rational tail, and real-seal handoff before any uniform-family consumer inspects it, so $U$ enters the selector-budget route through the same finite envelope.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-meet refusal fork]
\label{thm:cauchy-limit-seal-tail-meet-refusal-fork}
Every $\RealUp$ or $\CompletionUp$ consumer of the tail-budget meet has exactly one of the following two routes. Either it factors through the finite envelope consisting of the $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\UniformCauchyCriterionUp$ tail ledger, $\RealObservationBudgetUp$ rows, $\CauchyLimitSealUp$ seal row, and shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; or its request is routed to the visible refusal boundary for quotient stream, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, ambient completeness, or metric-completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_meet\_refusal\_fork}
\begin{proof}
First use the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. It supplies the common route over the selector read, observation-budget read, completion-consumer read, and shared structural rows.

Transport that common route with \autoref{thm:cauchy-limit-seal-selector-budget-transport}. The transported consumer still sees only the finite precision request, window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and naming rows.

Apply the consumer normal form of \autoref{thm:cauchy-limit-seal-tail-budget-consumer-normal-form} together with the root unblock of \autoref{thm:cauchy-limit-seal-completion-budget-root-unblock}. These results force every $\RealUp$ or $\CompletionUp$ read to enter the downstream surface through the displayed finite meet before any completion-facing inspection occurs.

Finally attach the uniform selector route from \autoref{thm:cauchy-limit-seal-tail-meet-uniform-selector-route}. Inspecting its envelope shows that quotient stream, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, ambient completeness, and metric-completeness are not coordinates of the finite route. A request for any such coordinate therefore cannot be served by the envelope and is sent to the visible refusal boundary.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-meet source exhaustion]
\label{thm:cauchy-limit-seal-tail-meet-source-exhaustion}
Every $\RealUp$ or $\CompletionUp$ consumer admitted by the tail-meet route exhausts exactly the finite source rows supplied by the $\CauchyLimitSealUp$ packet, the $\RealObservationBudgetUp$ packet, and the $\UniformCauchyCriterionUp$ packet. The exhausted rows are the shared $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\BHist$ histories, $\hsame$ transports, $\Cont$ continuations, $\Pkg$ provenance rows, and $\NameCert$ naming rows, together with the displayed seal, observation-budget, and uniform-tail coordinates named by those packets.

No admitted consumer may read an additional Real-completion source outside these finite rows. A request for quotient stream identity, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, ambient completeness, or metric-completeness is routed to the refusal boundary rather than to a second source envelope.
\end{theorem}
\begin{proof}
Begin with the uniform selector route of \autoref{thm:cauchy-limit-seal-tail-meet-uniform-selector-route}. It joins the $\CauchyLimitSealUp$, $\RealObservationBudgetUp$, and $\UniformCauchyCriterionUp$ packets over one finite envelope with the shared $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next apply the refusal fork \autoref{thm:cauchy-limit-seal-tail-meet-refusal-fork}. A $\RealUp$ or $\CompletionUp$ consumer is therefore either on that finite envelope or outside the admitted route, where the listed non-envelope requests are refused.

The exact source rows are fixed by \autoref{thm:cauchy-limit-seal-tail-budget-meet}. The meet binds the selector read, observation-budget read, and completion-consumer read to the same precision request, finite stream window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and naming rows.

Finally use the consumer normal form \autoref{thm:cauchy-limit-seal-tail-budget-consumer-normal-form}. Since every admitted consumer has that normal form and the fork refuses the alternatives, the route exhausts exactly the finite rows supplied by the three source packets and exposes no additional Real-completion source.
\end{proof}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_tail\_meet\_source\_exhaustion}

\begin{theorem}[CauchyLimitSeal tail-meet diagonal compatibility handoff]
\label{thm:cauchy-limit-seal-tail-meet-diagonal-compatibility-handoff}
Suppose an accepted $\CauchyLimitSealUp$ tail-meet route has finite envelope $E$, and suppose the same envelope is consumed by an accepted $\DiagonalLimitCompatibilityUp$ packet through its root formal handoff surface. Then the handoff boundary is exactly the shared $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal row, $\UniformCauchyCriterionUp$ tail ledger, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, together with the diagonal compatibility selector read from the accepted compatibility packet.

The handoff exposes no quotient stream, host real equality, selected external limit, hidden diagonal oracle, independent completion row, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. It identifies the common precision request, stream window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and naming rows that any admitted Real-completion consumer must read.

Transport the route through \autoref{thm:cauchy-limit-seal-selector-budget-transport}. The selector read stays inside the same finite envelope, so a downstream diagonal consumer sees the transported tail-meet rows rather than a second completion source.

Apply source exhaustion from \autoref{thm:cauchy-limit-seal-tail-meet-source-exhaustion}. The admitted route has already exhausted the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\UniformCauchyCriterionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows before the diagonal compatibility packet reads the envelope.

Finally read the root formal handoff surface of $\DiagonalLimitCompatibilityUp$. That surface contributes only the displayed diagonal compatibility selector and consumes the already exhausted envelope. Since quotient stream identity, host real equality, selected external limits, hidden diagonal oracles, independent completion rows, and ambient completeness coordinates are absent from both finite surfaces, none can cross the handoff boundary.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-meet diagonal source exhaustion]
\label{thm:cauchy-limit-seal-tail-meet-diagonal-source-exhaustion}
Every $\DiagonalLimitCompatibilityUp$ consumer of an accepted $\CauchyLimitSealUp$ tail-meet route exhausts exactly the shared $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal row, $\UniformCauchyCriterionUp$ tail ledger, $\RealObservationBudgetUp$ rows, diagonal selector row, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

No such consumer retains a coordinate for quotient stream identity, host real equality, a selected external limit, a hidden diagonal oracle, an independent completion row, ambient completeness, or metric completeness outside the accepted handoff surface.
\end{theorem}
\begin{proof}
First use source exhaustion for the tail meet, \autoref{thm:cauchy-limit-seal-tail-meet-source-exhaustion}. It fixes the accepted Real and completion route as the finite envelope over the shared stream window, regular-rational source row, dyadic ledger, Real seal, uniform tail ledger, observation-budget rows, and structural BEDC rows.

Next attach the uniform selector route of \autoref{thm:cauchy-limit-seal-tail-meet-uniform-selector-route}. This places the diagonal-facing selector read on the same finite route before any compatibility consumer receives the envelope.

Apply the diagonal compatibility handoff of \autoref{thm:cauchy-limit-seal-tail-meet-diagonal-compatibility-handoff} together with the root formal route of \autoref{thm:diagonal-limit-compatibility-root-formal-route}. The diagonal packet contributes only its displayed selector row and consumes the already bounded source route.

The refusal clauses in the handoff theorem then identify the absent coordinates. Quotient stream identity, host real equality, selected external limits, hidden diagonal oracles, independent completion rows, ambient completeness, and metric completeness are not fields of either finite surface, so the diagonal consumer exhausts exactly the listed shared rows.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-budget meet consumer determinacy]
\label{thm:cauchy-limit-seal-tail-budget-meet-consumer-determinacy}
Every $\RealUp$ or $\CompletionUp$ consumer admitted by the tail-budget meet is determined by the shared $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\RealObservationBudgetUp$ budget row, $\CauchyLimitSealUp$ seal row, $\UniformCauchyCriterionUp$ tail row, and the structural $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Two admitted consumers that agree on these rows have the same public Real-completion read, and no quotient stream identity, host real equality, selected external limit, hidden diagonal oracle, independent completion row, or ambient completeness coordinate can distinguish them.
\end{theorem}
\begin{proof}
Begin with the finite meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet}. It binds the selector read, observation-budget read, and completion-consumer read to one displayed envelope over the shared stream window, dyadic ledger, regular handoff, Real seal, transport, continuation, provenance, and naming rows.

Apply source exhaustion from \autoref{thm:cauchy-limit-seal-tail-meet-source-exhaustion}. The admitted Real or completion consumer has no second source outside the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealObservationBudgetUp$, $\CauchyLimitSealUp$, $\UniformCauchyCriterionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally use diagonal source exhaustion from \autoref{thm:cauchy-limit-seal-tail-meet-diagonal-source-exhaustion}. It identifies the same envelope after the diagonal-facing handoff, so agreement on the finite rows determines the public consumer read and leaves no absent coordinate able to separate the two consumers.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-budget meet ledger exhaustion]
\label{thm:cauchy-limit-seal-tail-budget-meet-ledger-exhaustion}
The ledger of an admitted $\RealUp$ or $\CompletionUp$ consumer of the tail-budget meet is exhausted by the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealObservationBudgetUp$, $\CauchyLimitSealUp$, $\UniformCauchyCriterionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed by the meet and its source-exhaustion theorems. After those rows are read, there is no remaining ledger coordinate for quotient stream identity, host real equality, selected external limits, hidden diagonal oracles, independent completion rows, ambient completeness, or metric completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchy-limit-seal-tail-budget-meet} to obtain the finite route binding the selector, budget, and completion reads. The ledger coordinates of that route are exactly the displayed stream, regular-rational, dyadic, Real, transport, continuation, provenance, and naming rows.

Refine the inventory with \autoref{thm:cauchy-limit-seal-tail-meet-source-exhaustion}. It adds the observation-budget and uniform-tail rows to the same finite envelope and refuses any second Real-completion source.

Then apply \autoref{thm:cauchy-limit-seal-tail-meet-diagonal-source-exhaustion}. The diagonal-facing consumer receives only the already exhausted rows plus the displayed selector row, so the listed non-envelope objects have no ledger position to occupy.
\end{proof}

\begin{theorem}[CauchyLimitSeal tail-budget meet Real handoff]
\label{thm:cauchy-limit-seal-tail-budget-meet-real-handoff}
The Real handoff exported by the tail-budget meet is exactly the finite route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealObservationBudgetUp$, $\CauchyLimitSealUp$, $\UniformCauchyCriterionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It cannot import quotient stream identity, host real equality, selected external limits, hidden diagonal oracles, independent completion rows, ambient completeness, or metric completeness into the $\RealUp$ or $\CompletionUp$ consumer boundary.
\end{theorem}
\begin{proof}
Start from the consumer determinacy theorem above. A Real or completion consumer is fixed by the shared finite envelope, so a handoff can expose only rows already present in that envelope.

Apply ledger exhaustion above. Once the stream, regular-rational, dyadic, budget, seal, uniform-tail, transport, continuation, provenance, and naming rows are consumed, there is no remaining field through which a quotient stream, host equality, selected limit, hidden diagonal oracle, independent completion row, ambient completeness, or metric completeness witness could enter.

The handoff is therefore the same finite Real-completion boundary described by the meet, source exhaustion, and diagonal source exhaustion rows, with no ambient completion principle imported from outside the accepted packets.
\end{proof}

\begin{corollary}[CauchyLimitSeal tail-budget meet strict local obstruction]
\label{cor:cauchy-limit-seal-tail-budget-meet-strict-local-obstruction}
Every displayed failure, refusal, separation, or countermodel row attached to the tail-budget meet is a strict local obstruction. If a $\RealUp$ or $\CompletionUp$ consumer of the meet asks for quotient stream identity, selected host limit, host real equality, hidden family limit, unbounded schedule, independent completion row, ambient completeness, or metric-completeness, then the row blocks exactly that requested converse or reuse route outside the displayed finite envelope. The same row does not assert a global impossibility theorem, does not supply a host-level theorem about all Cauchy limits, and does not act as hidden external validation for any completion principle.
\end{corollary}
\begin{proof}
Apply the refusal fork of \autoref{thm:cauchy-limit-seal-tail-meet-refusal-fork}. It gives exactly two consumer-facing alternatives for the tail-budget meet. The consumer either factors through the finite envelope consisting of the $\StreamNameUp$ window, $\RegSeqRatUp$ source row, $\DyadicRatCoreUp$ ledger, $\UniformCauchyCriterionUp$ tail ledger, $\RealObservationBudgetUp$ rows, $\CauchyLimitSealUp$ seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, or its request is routed to the visible refusal boundary for one of the listed non-envelope coordinates.

Use selector-budget transport from \autoref{thm:cauchy-limit-seal-selector-budget-transport} to identify the stable part of the admitted route. Transport preserves the same precision request, finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ handoff, $\RealUp$ seal, $\BHist$ surface, $\Pkg$ provenance, and local $\NameCert$ row. Thus a transported selector read, budget read, or completion-facing read remains inside the displayed finite packet and gains no quotient stream identity, host real equality, choice-selected limit, hidden family limit, or ambient completeness coordinate.

Now inspect an obstruction row. If the requested coordinate is one of the listed non-envelope coordinates, the fork sends that coordinate to the refusal boundary because it is not a field of the finite envelope. If the requested coordinate is one of the envelope coordinates, transport keeps the request inside the admitted selector-budget packet and the obstruction row is not invoked. Therefore the row blocks only the named converse or reuse route that tries to read beyond the displayed packet.

This locality also fixes the interpretation of the obstruction. The proof has used only the finite envelope and the transported selector-budget packet, so the obstruction has no quantifier over all host Cauchy limits, no host theorem surface, and no external validation coordinate. It records that the specified consumer request cannot be served by this tail-budget meet route; it does not claim that the requested object is globally impossible or that an ambient completion principle has been validated elsewhere.
\end{proof}
