\chapter{A Concrete Naming Certificate for $\MetaCICParallelDiamondFrontierUp$}
\label{ch:concrete-instances-metacic-parallel-diamond-frontier-namecert}
\origin{ai}

The $\MetaCICParallelDiamondFrontierUp$ packet realizes the residual-substitution frontier of \autoref{ch:metacic-confluence-audit-map} as finite confluence-facing NameCert data. It sits beside the residual-substitution boundary of \autoref{ch:concrete-instances-metacic-residual-substitution-boundary-namecert}, the confluence critical-pair boundary of \autoref{ch:concrete-instances-metacic-confluence-critical-pair-boundary-namecert}, the closed checker seal of \autoref{ch:concrete-instances-closed-type-checker-seal-namecert}, and the closed-normal confluence fragment of \autoref{ch:concrete-instances-metacicconfluencenormalfragment-namecert}. The packet records the conditional parallel-diamond frontier without claiming residual-substitution compatibility, full closed Church--Rosser, subject reduction, evaluator equality, or kernel consistency.

\falsifiablePrediction{Every accepted $\MetaCICParallelDiamondFrontierUp$ confluence-facing read exposes the residual-substitution premise row before any parallel-diamond handoff can be consumed.}

\independenceWitness{metacic-residual-substitution-boundary, metacic-confluence-critical-pair-boundary, closed-type-checker-seal, metacicconfluencenormalfragment: the residual-substitution boundary names the missing compatibility input without the parallel-diamond handoff; the critical-pair boundary records local peak data without the closed checker seal; the closed type-checker seal records bounded checking without confluence closure; and the closed-normal fragment records unconditional normal-source joins without the residual frontier. None is bijective to $\MetaCICParallelDiamondFrontierUp$.}

\begin{definition}[MetaCIC parallel-diamond frontier carrier]
\label{def:metacic-parallel-diamond-frontier-carrier}
A $\MetaCICParallelDiamondFrontierUp$ carrier is a finite $\BHist$ packet
$$
F=(P,K,J,R,S,C,B,O,H,T,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the residual-substitution premise row, naming the substitution compatibility input required by the parallel-diamond route.
\item $K$ is the critical-pair row, recording the local peak and its two parallel-reduction observations.
\item $J$ is the candidate-join row, recording the proposed common reduct and branch-local route requests.
\item $R$ is the residual-frontier row, listing residual descendants, binder-depth exposure, and branch-local substitution windows.
\item $S$ is the closed type-checker seal row consumed before a closed confluence-facing read can use the checker data.
\item $C$ is the closed-normal fragment row, recording the already available normal-source and atom-source confluence fragments.
\item $B$ is the bounded-check row over closedness, support, branch compatibility, and finished-normalization boundaries.
\item $O$ is the obstruction row naming the endpoints not supplied by the packet: residual-substitution discharge, full parallel diamond, subject reduction, arbitrary closed Church--Rosser, evaluator equality, and kernel consistency.
\item $H$ records componentwise $\hsame$ transport for premise, peak, join, residual, checker, fragment, bounded-check, obstruction, replay, provenance, and local naming rows.
\item $T$ records displayed $\Cont$ replay from a confluence query through $P,K,J,R,S,C,B,O,H,G,N$.
\item $G$ is the $\Pkg$ provenance over $\MetaCICParallelDiamondFrontierUp$, $\MetaCICResidualSubstitutionBoundaryUp$, $\MetaCICConfluenceCriticalPairBoundaryUp$, $\ClosedTypeCheckerSealUp$, $\MetaCICConfluenceNormalFragmentUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetaCICParallelDiamondFrontierUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $P,K,J,R,S,C,B,O,H,T,G,N$. It has no coordinate for a premise-free parallel diamond, subject reduction, arbitrary closed Church--Rosser, unrestricted beta-conversion decidability, evaluator equality, quotient equality of terms, or kernel consistency.
\end{definition}

\begin{theorem}[MetaCIC parallel-diamond frontier obligations]
\label{thm:metacic-parallel-diamond-frontier-obligations}
For every accepted $\MetaCICParallelDiamondFrontierUp$ carrier
$$
F=(P,K,J,R,S,C,B,O,H,T,G,N),
$$
the local $\NameCert_{\MetaCICParallelDiamondFrontierUp}$ surface consists exactly of residual-substitution premise retention through $P$, critical-pair exposure through $K$, candidate-join exposure through $J$, residual-frontier exposure through $R$, closed-checker handoff through $S$, closed-normal fragment exposure through $C$, bounded-check exposure through $B$, obstruction retention through $O$, componentwise transport through $H$, displayed replay through $T$, provenance through $G$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-parallel-diamond-frontier-carrier}. The confluence-facing rows are $P,K,J,R,S,C,B,O$, and the structural certificate rows are $H,T,G,N$.

The residual-substitution premise row remains first-class. Row $P$ is not discharged by the carrier; it is the named input that the conditional parallel-diamond route must still expose.

The local geometry is then displayed through $K,J,R$. The critical-pair, candidate-join, and residual-frontier rows provide finite peak data and branch-local residual windows, while the closed checker and closed-normal rows show which existing fragments may be consumed.

Finally $B,O,H,T,G,N$ keep the bounded checks, obstruction endpoints, transport, replay, provenance, and local naming attached to the same packet. Since no omitted theorem appears as a carrier coordinate, the listed rows exhaust the frontier obligations.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond frontier handoff]
\label{thm:metacic-parallel-diamond-frontier-handoff}
Every confluence consumer of an accepted $\MetaCICParallelDiamondFrontierUp$ packet must expose the residual-substitution premise row $P$, the critical-pair row $K$, the candidate-join row $J$, the residual-frontier row $R$, the closed checker seal row $S$, the closed-normal fragment row $C$, and the bounded-check row $B$ before any parallel-diamond handoff is read. The handoff may feed the conditional route recorded in \autoref{ch:metacic-confluence-audit-map}, but it does not discharge residual substitution, prove subject reduction, prove arbitrary closed confluence, decide evaluator equality, or establish kernel consistency.
\end{theorem}
\begin{proof}
Begin with the obligation surface of \autoref{thm:metacic-parallel-diamond-frontier-obligations}. It forces every confluence read through the named premise, peak, join, residual, checker, fragment, bounded-check, and obstruction rows.

The sibling packets preserve that boundary. The residual-substitution boundary supplies the named premise, the critical-pair boundary supplies local peak data, the closed type-checker seal supplies bounded checker data, and the normal fragment supplies only the closed-normal and atom-source cases already available.

The obstruction row $O$ remains part of the packet. Therefore the handoff is a finite frontier certificate for a conditional route, not a proof of the missing residual-substitution input or any stronger confluence endpoint.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond frontier route]
\label{thm:metacic-parallel-diamond-frontier-route}
Every confluence-audit consumer that reads an accepted $\MetaCICParallelDiamondFrontierUp$ packet must expose the residual-substitution premise row $P$, critical-pair row $K$, candidate-join row $J$, residual-frontier row $R$, closed-checker seal $S$, closed-normal fragment $C$, bounded-check row $B$, obstruction row $O$, transport row $H$, replay row $T$, provenance row $G$, and local name row $N$ before using a conditional parallel-diamond handoff. The route does not turn the residual-substitution premise into a theorem, does not prove full Church--Rosser, and does not discharge subject reduction, evaluator equality, quotient term equality, or kernel consistency.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:metacic-parallel-diamond-frontier-carrier}. It displays exactly the premise, peak, join, residual, checker, fragment, bounded-check, obstruction, transport, replay, provenance, and local naming rows.

The obligation theorem \autoref{thm:metacic-parallel-diamond-frontier-obligations} keeps $P,K,J,R,S,C,B,O$ as first-class rows. A confluence-audit consumer therefore cannot use the handoff before the missing residual-substitution premise and the obstruction boundary are visible.

The handoff theorem \autoref{thm:metacic-parallel-diamond-frontier-handoff} supplies only a conditional frontier route. The added transport, replay, provenance, and local name rows preserve that boundary for downstream audit consumers.

Since no row discharges residual substitution or full closed confluence, the route is a sharper obligation boundary rather than a completed Church--Rosser certificate.
\end{proof}

\begin{theorem}[MetaCIC local-diamond frontier]
\label{thm:metacic-local-diamond-frontier}
Let
$$
F_0=(P,K,J_0,R,S,C,B,O,H,T,G,N)
\quad\text{and}\quad
F_1=(P,K,J_1,R,S,C,B,O,H,T,G,N)
$$
be accepted $\MetaCICParallelDiamondFrontierUp$ packets with the same residual-substitution premise row $P$ and the same critical-pair row $K$. If the candidate-join rows $J_0$ and $J_1$ agree through the displayed residual-frontier row $R$, then every confluence-audit consumer reads the same conditional local-diamond handoff through $S,C,B,O,H,T,G,N$. The obstruction row $O$ remains visible in the handoff, so the result does not discharge residual-substitution compatibility, subject reduction, full closed Church--Rosser, evaluator equality, quotient equality of terms, or kernel consistency.
\end{theorem}
\begin{proof}
Project the two carriers through \autoref{def:metacic-parallel-diamond-frontier-carrier}. The hypotheses identify the premise and peak rows $P,K$, and they make the two candidate-join rows agree at the residual-frontier row $R$.

Apply \autoref{thm:metacic-parallel-diamond-frontier-obligations} to each packet. The only confluence-facing rows available to a consumer before replay are $P,K,J,R,S,C,B,O$, with the structural rows $H,T,G,N$ attached to the same packet.

Now use \autoref{thm:metacic-parallel-diamond-frontier-handoff} and \autoref{thm:metacic-parallel-diamond-frontier-route}. Since $P,K$ agree and $J_0,J_1$ agree through $R$, both handoff readings reach the same closed-checker row $S$, closed-normal fragment row $C$, bounded-check row $B$, obstruction row $O$, transport row $H$, replay row $T$, provenance row $G$, and local name row $N$.

The obstruction row is not removed by this comparison. It is carried in both packets and remains part of the consumer-visible handoff, so the theorem records a local-diamond frontier fact rather than a proof of the missing residual-substitution or closed confluence endpoints.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond residual-substitution scope]
\label{thm:metacic-parallel-diamond-frontier-residual-substitution-scope}
Every use of the $\MetaCICParallelDiamondFrontierUp$ local-diamond frontier must pass through the residual-substitution boundary, the confluence critical-pair boundary, and the closed-normal fragment before it claims a local join. In carrier terms, a consumer must expose the residual-substitution premise row $P$, the critical-pair row $K$, the residual-frontier row $R$, the closed checker seal row $S$, and the closed-normal fragment row $C$ before reading the candidate-join handoff. The resulting claim remains a local frontier claim; it does not close full Church--Rosser, subject reduction, evaluator equality, quotient equality of terms, or kernel consistency.
\end{theorem}
\begin{proof}
Apply the route theorem \autoref{thm:metacic-parallel-diamond-frontier-route}. It requires the residual-substitution premise row, the critical-pair row, the residual-frontier row, the closed-checker seal, and the closed-normal fragment to remain visible before the conditional handoff is consumed.

Then apply the local-diamond frontier theorem \autoref{thm:metacic-local-diamond-frontier}. The agreement of candidate-join rows is read only through the displayed residual-frontier row, and the obstruction row remains visible in the handoff.

The sibling boundaries named in the chapter introduction supply exactly the surrounding scope: the residual-substitution boundary names the missing compatibility premise, the confluence critical-pair boundary names the local peak surface, and the closed-normal fragment names the already available normal-source joins. Since none of these rows removes the obstruction row, the theorem records a residual-substitution-scoped local join rather than any stronger confluence endpoint.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond frontier premise retention]
\label{thm:metacic-parallel-diamond-frontier-premise-retention}
Any accepted $\MetaCICParallelDiamondFrontierUp$ packet whose local-diamond handoff is consumed retains the residual-substitution premise row $P$ through the critical-pair row $K$, residual-frontier row $R$, closed-checker row $S$, and closed-normal row $C$. No consumer may reinterpret that handoff as residual-substitution compatibility, premise-free parallel diamond, full Church--Rosser, subject reduction, evaluator equality, quotient equality of terms, or kernel consistency.
\end{theorem}
\begin{proof}
Apply the obligations theorem \autoref{thm:metacic-parallel-diamond-frontier-obligations}. It makes $P$ a first-class residual-substitution premise row and keeps $K,R,S,C$ among the confluence-facing rows rather than structural metadata.

Next use the handoff and route theorems, \autoref{thm:metacic-parallel-diamond-frontier-handoff} and \autoref{thm:metacic-parallel-diamond-frontier-route}. They require a consumer to expose the premise, critical-pair, residual-frontier, checker, and closed-normal rows before the conditional handoff is read.

Finally apply the residual-substitution scope theorem \autoref{thm:metacic-parallel-diamond-frontier-residual-substitution-scope}. Since the local-diamond frontier remains scoped by the residual-substitution boundary and the obstruction row is still visible, the retained handoff cannot be retyped as any of the refused confluence endpoints.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond frontier discharge obstruction]
\label{thm:metacic-parallel-diamond-frontier-discharge-obstruction}
Any accepted $\MetaCICParallelDiamondFrontierUp$ packet consumed as a local-diamond handoff still exposes the residual-substitution premise row $P$ and obstruction row $O$. Unless a separate $\MetaCICResidualSubstitutionCompatibilityUp$ certificate is supplied through \autoref{ch:concrete-instances-metacic-residual-substitution-compatibility-namecert}, no consumer may read that handoff as a premise-free parallel diamond, full closed confluence, subject reduction, evaluator equality, quotient term equality, or kernel consistency.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-parallel-diamond-frontier-carrier}. The rows $P$ and $O$ are displayed coordinates of the accepted packet, not annotations around the handoff.

Apply premise retention, \autoref{thm:metacic-parallel-diamond-frontier-premise-retention}. It keeps $P$ visible through the critical-pair, residual-frontier, closed-checker, and closed-normal rows whenever the local-diamond handoff is consumed.

Now use the sibling route theorem \autoref{thm:metacic-parallel-diamond-frontier-sibling-route}. The exported contribution is exactly retained premise and obstruction data for confluence-facing siblings, so the handoff cannot be consumed as a premise-free diamond.

The only admissible discharge surface is the residual-substitution compatibility chapter named in the statement. Without that separate certificate, the obstruction row $O$ continues to block full closed confluence, subject reduction, evaluator equality, quotient term equality, and kernel consistency.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond closed-checker retention]
\label{thm:metacic-parallel-diamond-closed-checker-retention}
Any accepted $\MetaCICParallelDiamondFrontierUp$ packet whose local-diamond handoff retains the residual-substitution premise row $P$ must also retain the closed-checker seal row $S$ and the closed-normal fragment row $C$ before that handoff can be read. Thus the conditional handoff boundary is the joint row surface $P,S,C$ together with the displayed critical-pair, residual-frontier, bounded-check, obstruction, transport, replay, provenance, and local naming rows. It is not a proof of residual substitution, subject reduction, evaluator equality, quotient term equality, or kernel consistency.
\end{theorem}
\begin{proof}
Apply the obligations theorem \autoref{thm:metacic-parallel-diamond-frontier-obligations}. It lists $P,S,C$ as confluence-facing rows of the same accepted carrier, so the checker seal and closed-normal fragment are not optional metadata around the premise row.

Next apply the handoff and route theorems, \autoref{thm:metacic-parallel-diamond-frontier-handoff} and \autoref{thm:metacic-parallel-diamond-frontier-route}. Both require the closed-checker seal and closed-normal fragment to be exposed before any conditional parallel-diamond handoff is consumed.

Finally use premise retention, \autoref{thm:metacic-parallel-diamond-frontier-premise-retention}. Since the retained premise row is read through $K,R,S,C$ and the obstruction row remains visible, the closed-checker seal and closed-normal fragment remain part of the boundary rather than consequences of the handoff. The refused endpoints therefore stay outside the packet.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond frontier sibling route]
\label{thm:metacic-parallel-diamond-frontier-sibling-route}
Every accepted $\MetaCICParallelDiamondFrontierUp$ packet that exports its premise-retention handoff feeds two confluence-facing sibling routes: the candidate-normalization confluence handoff of \autoref{ch:concrete-instances-metacic-candidate-normalization-confluence-handoff-namecert} and the audit-packet boundary of \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}. The exported contribution is exactly the residual-substitution premise row $P$, the local critical-pair row $K$, the residual-frontier row $R$, and the obstruction row $O$ retained by \autoref{thm:metacic-parallel-diamond-frontier-premise-retention}; it does not supply a premise-free diamond, a completed residual-substitution theorem, full closed confluence, subject reduction, evaluator equality, quotient equality of terms, or kernel consistency.
\end{theorem}
\begin{proof}
Apply \autoref{thm:metacic-parallel-diamond-frontier-premise-retention}. Any consumed local-diamond handoff keeps the residual-substitution premise row visible through the critical-pair, residual-frontier, closed-checker, and closed-normal rows.

The candidate-normalization confluence handoff can therefore read this packet only as retained frontier data: $P$ names the missing residual-substitution input, $K$ and $R$ name the local peak and residual window, and $O$ keeps the obstruction endpoints visible before candidate-normalization routes are consumed.

The confluence audit packet reads the same rows as an audit boundary. It can cite the retained premise and obstruction rows when it records a conditional local-diamond route, but it cannot erase them into a completed confluence theorem.

Thus the sibling lattice is substantive rather than bibliographic: the frontier supplies exactly the residual-substitution premise retention and local-diamond obstruction rows consumed by those confluence-facing packets, while the refused endpoints remain outside the carrier.
\end{proof}

\begin{theorem}[MetaCIC parallel-diamond confluence handoff]
\label{thm:metacic-parallel-diamond-confluence-handoff}
An accepted $\MetaCICParallelDiamondFrontierUp$ packet whose local-diamond, premise-retention, and residual-substitution rows have been displayed exports exactly the conditional confluence handoff consumed by \autoref{ch:concrete-instances-metacic-candidate-normalization-confluence-handoff-namecert} and bounded by \autoref{ch:concrete-instances-parallel-diamond-residual-namecert}. In carrier terms, the handoff is the retained route through $P,K,J,R,S,C,B,O,H,T,G,N$: $P$ remains the residual-substitution premise, $K,J,R$ expose the local-diamond and residual windows, $S,C,B$ keep the closed checker and bounded fragment visible, and $O$ records the still-open endpoints. The handoff does not claim global confluence, full strong normalization, subject reduction, evaluator equality, quotient equality of terms, or kernel consistency.
\end{theorem}
\begin{proof}
Project the frontier carrier. The rows $P,K,J,R,S,C,B,O$ are the confluence-facing data, while $H,T,G,N$ transport, replay, source, and name the same packet.

Apply \autoref{thm:metacic-parallel-diamond-frontier-premise-retention}. The residual-substitution premise row $P$ is retained through the local critical-pair and residual-frontier rows, so the exported route cannot be read as a premise-free diamond.

Next use \autoref{thm:metacic-parallel-diamond-frontier-discharge-obstruction}. It keeps the obstruction row $O$ visible unless a separate residual-substitution compatibility certificate is supplied, and therefore preserves the boundary checked by the parallel-diamond residual packet.

Finally apply the sibling route theorem. The candidate-normalization handoff receives only the closed checker boundary, local-diamond window, residual ledger, retained premise, and obstruction data displayed by this packet. Since no carrier row contains global confluence, full strong normalization, subject reduction, evaluator equality, quotient equality, or kernel consistency, none of those endpoints is exported by the handoff.
\end{proof}

The Lean follow-up supplies $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ TasteGate instances in \texttt{lean4/BEDC/Derived/MetaCICParallelDiamondFrontierUp/TasteGate.lean} by exhibiting distinct accepted and refused frontier packets and by matching on the rows $P,K,J,R,S,C,B,O,H,T,G,N$.

\closureat{MetaCICParallelDiamondFrontierUp}{seedStr}

\begin{closurestatus}{\MetaCICParallelDiamondFrontierUp}
  \constructivestory{A $\MetaCICParallelDiamondFrontierUp$ packet is generated from residual-substitution premise rows, critical-pair rows, candidate-join rows, residual-frontier rows, closed checker seal rows, closed-normal fragment rows, bounded-check rows, obstruction rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-parallel-diamond-frontier-carrier}, \autoref{thm:metacic-parallel-diamond-frontier-obligations}, and \autoref{thm:metacic-parallel-diamond-frontier-handoff} seed the conditional parallel-diamond frontier packet for MetaCIC confluence consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close residual-substitution compatibility, full parallel diamond, subject reduction, arbitrary closed Church--Rosser, evaluator equality, quotient equality of terms, kernel consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, residual-substitution premise retention, critical-pair exposure, candidate-join exactness, residual-frontier coverage, closed-checker handoff, closed-normal fragment routing, bounded-check exactness, obstruction retention, TasteGate nontriviality, FieldFaithful coverage, transport, replay, provenance, and local naming for BEDC.Derived.MetaCICParallelDiamondFrontierUp.}
\end{closurestatus}
