\begin{theorem}[MetaCIC critical-path candidate schedule discharge]
\label{thm:metacic-criticalpath-candidate-schedule-discharge}
Let
$$
K=(S,N,O,U,D,H,C,P,L)
$$
be an accepted $\MetaCICCriticalPathUp$ root-unblock packet. A candidate-mediated schedule for strong normalization and confluence can discharge the open route only after it exposes candidate-set normalization, a critical-pair ledger, a residual-substitution boundary, finite observation confluence, and subject-reduction socket rows through the same packet. The schedule cannot cite unbounded confluence, global strong normalization, hidden substitution principles, quotient term equality, or ambient metatheoretic consistency as discharge data.
\end{theorem}
\begin{proof}
Begin with the candidate-mediated SN obligation surface, \autoref{thm:metacic-confluence-candidate-mediated-sn-obligation-surface}. It forces candidate-mediated normalization reads to display the strong-normalization row, normal-form endpoint, handoff row, discharge socket, transport, replay, provenance, local name, and the four L10 faces before confluence or decidability budgets are consumed.

Next expose the finite schedule rows. The candidate-discharge frontier of \autoref{thm:metacic-critical-path-candidate-discharge-frontier} keeps the subject-reduction obstruction row $O$ and discharge socket $D$ visible, while the dependency-exposure rows of \autoref{thm:metacic-critical-path-normalization-frontier-dependency-exposure} and \autoref{thm:metacic-critical-path-confluence-audit-dependency-exposure} keep candidate-set normalization, critical-pair ledgers, residual-substitution boundaries, finite observation confluence, and subject-reduction sockets as named dependencies rather than hidden assumptions.

Finally apply the confluence-decidability handoff exhaustion of \autoref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It permits bounded consumers to read the candidate schedule only through the displayed packet and refuses full confluence, global strong normalization, hidden substitution, quotient equality, and consistency exports.

Thus a candidate-mediated schedule can discharge only the rows it displays. Without the five named schedule rows, the open socket remains a boundary rather than a completed metatheorem.
\end{proof}
