\begin{theorem}[MetaCIC critical-path confluence-decidability handoff exhaustion]
\label{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
every confluence-facing or decidability-facing downstream read of $U$ factors through the displayed rows $O,D,H,C,P,L$ together with the finite packet rows $S,N,U$. The handoff exports no arbitrary Church--Rosser theorem, no global beta-conversion decision procedure, no closed subject reduction, and no full closed consistency.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathConfluenceDecidabilityHandoffExhaustion}
\begin{proof}
Start with the socket theorem. By \autoref{thm:metacic-critical-path-confluence-decidability-socket}, every confluence-facing or decidability-facing use of the handoff row is mediated by the obstruction, discharge socket, transport, route, provenance, and local naming rows $O,D,H,C,P,L$.

Next exhaust the packet route. The handoff exhaustion theorem \autoref{thm:metacic-critical-path-handoff-exhaustion} says that the finite route has only the rows $S,N,O,U,D,H,C,P,L$ and contains no coordinate for closed subject reduction, full closed consistency, global beta-conversion decidability, or quotient term equality.

The local socket boundary supplies the negative side. Apply \autoref{thm:metacic-critical-path-discharge-socket-locality} to keep $D$ local to $H,C,P,L$ and separate from any hidden discharge, then apply \autoref{thm:metacic-critical-path-normalization-obstruction-route-coverage} to keep the obstruction row visible along normalization-to-normal-form reads.

Therefore a downstream read of $U$ has only the displayed finite data available: $O,D,H,C,P,L$ for the socket-mediated handoff and $S,N,U$ for the remaining packet coordinates. Since no further theorem-export coordinate is present, the four excluded metatheoretic claims remain outside the handoff.
\end{proof}

\begin{theorem}[MetaCIC critical-path candidate-mediated SN boundary]
\label{thm:metacic-critical-path-candidate-mediated-sn-boundary}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any candidate-mediated strong-normalization-facing read of the handoff row factors through the displayed packet rows $S,N,O,U,D,H,C,P,L$ together with the four Phase Real faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ recorded by Definition~\ref{def:metacic-critical-path-open-phase-source-ledger}. The read exports no arbitrary strong-normalization theorem, no Church--Rosser theorem, no beta-conversion decision procedure, no quotient term equality, no host real equality, no selected limit, and no $\RealUp$ completeness claim.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathCandidateMediatedSNBoundary}
\begin{proof}
First apply the confluence-decidability handoff exhaustion theorem, Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It bounds every confluence-facing or decidability-facing use of the handoff row by the mediated rows $O,D,H,C,P,L$ and the remaining packet coordinates $S,N,U$.

Next attach the current Phase Real source surface. The open-phase source closure theorem, Theorem~\ref{thm:metacic-critical-path-open-phase-source-closure}, says that admitted source reads factor through the displayed packet rows and one of the four rows $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$. The open-phase consumer totality theorem, Theorem~\ref{thm:metacic-critical-path-open-phase-consumer-totality}, says that current Phase Real and Completion consumers receive the ledger as their whole source surface.

Finally use the nonescape side of the ledger. Theorem~\ref{thm:metacic-critical-path-phase-real-root-unblock-soundness} and Theorem~\ref{thm:metacic-critical-path-open-phase-source-nonescape} exclude quotient real data, host equality, selected limits, countable choice, trichotomy, open-cover compactness, $\RealUp$ completeness, closed subject reduction, and full consistency from the admitted route. Since a candidate-mediated strong-normalization-facing read has no additional coordinate beyond the same packet rows and four ledger faces, the listed SN, Church--Rosser, beta-conversion, quotient, host-equality, selected-limit, and completeness claims remain outside the handoff.
\end{proof}

\begin{theorem}[MetaCIC candidate-mediated SN four-face audit precondition]
\label{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any candidate-mediated strong-normalization-facing read that is also consumed as current Phase $\RealUp$ and Completion evidence must first expose the four local face records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Each face must carry its own scoped-closure row and its own audit-clean verification row, and the shared support may use only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. The candidate-mediated SN row supplies no aggregate formalstatus, no aggregate leantarget, no aggregate bridge row, no quotient stream equality, no selected limit, no countable-choice row, no metric-completeness datum, and no $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Begin with the SN-facing route. The candidate-mediated boundary theorem, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}, sends every such read through the finite packet rows $S,N,O,U,D,H,C,P,L$ and the four Phase Real faces listed in Definition~\ref{def:metacic-critical-path-open-phase-source-ledger}.

Next read those faces as the source surface for current Phase Real and Completion consumption. Definition~\ref{def:metacic-critical-path-open-phase-source-ledger}, Theorem~\ref{thm:metacic-critical-path-open-phase-source-closure}, and Theorem~\ref{thm:metacic-critical-path-open-phase-consumer-totality} restrict the consumer to the displayed packet rows and the four local faces; no fifth source row or hidden discharge coordinate is introduced.

Now apply the current exit threshold. Theorem~\ref{thm:real-l10-current-phase-exit-local-threshold} identifies the consumed evidence with the objectwise product of the four local threshold records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, supported only by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Finally use the StreamName audit readback. Theorem~\ref{thm:streamname-four-face-audit-clean-threshold-readback} reads the same threshold through face-local audit rows rather than through a route-level credential. Therefore a candidate-mediated SN read that is consumed by the current Phase Real and Completion surface must display the four separate scoped-closure and audit-clean rows, and the aggregate status, leantarget, bridge, quotient, choice, metric-completeness, selected-limit, and $\RealUp$ completeness data remain outside the route.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathCandidateSNFourFaceAuditPrecondition}

\begin{theorem}[MetaCIC four-face discharge precondition strengthening]
\label{thm:metacic-critical-path-four-face-discharge-precondition-strengthening}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any candidate-mediated strong-normalization-facing read that satisfies the four-face audit precondition can be consumed by the current Phase $\RealUp$ and Completion surface only while the separate discharge socket row $D$ remains visible as an unmet row distinct from the four L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The four-face audit product cannot be read as a discharge of $D$, closed subject reduction, full consistency, global beta-conversion decidability, quotient term equality, host equality, a selected limit, or $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathFourFaceDischargePreconditionStrengthening}
\begin{proof}
Start with the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. It exposes the four local scoped-closure and audit-clean face records as the only current Phase $\RealUp$ and Completion source surface supplied by the candidate-mediated SN read.

Next apply the candidate route discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}. That result keeps $D$ as the displayed discharge socket coordinate and denies any witness that fills it, even after the four audit faces are present.

Finally use the candidate SN socket nonescape theorem, Theorem~\ref{thm:metacic-critical-path-candidate-sn-socket-nonescape}. It prevents downstream consumers from absorbing $D$ into the four-face route or into a closed metatheoretic theorem. Therefore the read remains consumable only with $D$ still visible as a separate unmet row, and the listed subject-reduction, consistency, beta-conversion, quotient, host-equality, selected-limit, and completeness claims stay outside the packet.
\end{proof}

\begin{theorem}[MetaCIC candidate route discharge refusal]
\label{thm:metacic-critical-path-candidate-route-discharge-refusal}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any candidate-mediated strong-normalization-facing read that satisfies the four-face audit precondition still treats $D$ only as the displayed discharge socket coordinate. The route supplies no witness that fills $D$, no closed subject-reduction theorem, and no full closed-consistency theorem.
\end{theorem}
\begin{proof}
Start with the candidate-mediated boundary. Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary} keeps the SN-facing read on the finite packet rows $S,N,O,U,D,H,C,P,L$ and the four local Phase Real faces.

Next impose the audit precondition. Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition} says that consumption as current Phase $\RealUp$ and Completion evidence exposes only the four separate scoped-closure and audit-clean face rows, supported by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. It does not add an aggregate discharge credential.

Now apply the handoff exhaustion and root-unblock boundaries. Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion} leaves closed subject reduction and full closed consistency outside the confluence-decidability route, while Theorem~\ref{thm:metacic-critical-path-phase-real-root-unblock-soundness} gives the same exclusion for the current Phase Real root-unblock route.

Therefore the candidate-mediated SN route can guide the local handoff and audit read, but it cannot turn the socket coordinate $D$ into a discharged witness or export the closed subject-reduction and full-consistency theorems.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathCandidateRouteDischargeRefusal}

\begin{theorem}[MetaCIC candidate SN socket nonescape]
\label{thm:metacic-critical-path-candidate-sn-socket-nonescape}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
every downstream consumer using the candidate-mediated strong-normalization route receives only the socket-aware finite route over $S,N,O,U,D,H,C,P,L$ together with the four local face rows for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The coordinate $D$ remains a separate discharge socket and is not absorbed into the four-face route, the consumer surface, closed subject reduction, or full closed consistency.
\end{theorem}
\begin{proof}
First separate the socket from the faces. Theorem~\ref{thm:metacic-critical-path-four-face-socket-separation} keeps the four Phase Real face records and the discharge socket as distinct obligations; neither side fills or promotes the other.

Next use source nonescape. Theorem~\ref{thm:metacic-critical-path-open-phase-source-nonescape} prevents admitted Phase Real and Completion reads from bypassing the displayed packet and face rows through quotient real data, host equality, selected limits, countable choice, trichotomy, open-cover compactness, or $\RealUp$ completeness.

Finally apply the discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}. It prevents the candidate-mediated SN route from filling $D$ or exporting closed subject reduction and full closed consistency. Hence every downstream consumer receives exactly the finite socket-aware route and the four local face rows, with $D$ still recorded as its own socket coordinate.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathCandidateSNSocketNonescape}

\begin{theorem}[MetaCIC candidate SN finite socket normal form]
\label{thm:metacic-critical-path-candidate-sn-finite-socket-normal-form}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
a candidate-mediated strong-normalization-facing read is consumable by the current Phase $\RealUp$ and Completion surface exactly when it displays the finite socket-aware rows $S,N,O,U,D,H,C,P,L$ together with the four local face records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, with support only from $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. This normal form exports no arbitrary strong-normalization theorem, no Church--Rosser theorem, no beta-conversion decidability, no quotient term equality, no host equality, no selected limit, no countable choice, no closed subject reduction, no full consistency theorem, no metric-completeness datum, and no $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
For the forward direction, start with the candidate-mediated SN boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It places every candidate-mediated read on the finite packet rows $S,N,O,U,D,H,C,P,L$ and the four local Phase Real faces.

Next impose the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. The current Phase $\RealUp$ and Completion consumer can read those faces only through separate local scoped-closure and audit records, carried by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The current exit threshold, Theorem~\ref{thm:real-l10-current-phase-exit-local-threshold}, identifies this as the objectwise four-face threshold surface rather than as an aggregate metatheoretic credential.

The negative coordinates are then exhausted by the socket and source boundaries. The discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}, keeps $D$ as a socket coordinate and refuses closed subject reduction and full consistency. The socket nonescape theorem, Theorem~\ref{thm:metacic-critical-path-candidate-sn-socket-nonescape}, keeps downstream consumers on the same finite route, while the open-phase source closure and nonescape theorems, Theorems~\ref{thm:metacic-critical-path-open-phase-source-closure} and~\ref{thm:metacic-critical-path-open-phase-source-nonescape}, exclude off-packet quotient, host-equality, selected-limit, choice, metric-completeness, and $\RealUp$ completeness data.

For the reverse direction, suppose the displayed finite socket-aware rows and four local face records are present with only the stated BEDC support. The open-phase consumer totality theorem, Theorem~\ref{thm:metacic-critical-path-open-phase-consumer-totality}, admits exactly this finite ledger as the current consumer surface, and Theorem~\ref{thm:real-l10-current-phase-exit-local-threshold} reads the four faces as the local threshold certificate. Since the cited refusal and nonescape theorems leave no hidden socket discharge or off-route coordinate, this displayed data is sufficient for current Phase $\RealUp$ and Completion consumption of the candidate-mediated read.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathCandidateSNFiniteSocketNormalForm}

\begin{theorem}[MetaCIC critical-path candidate decider exhaustion]
\label{thm:metacic-critical-path-candidate-decider-exhaustion}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
every beta-conversion read or decidability-facing read mediated by the candidate strong-normalization route is confined to the finite socket rows $S,N,O,U,D,H,C,P,L$ together with the four L10 face records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The route exports no global beta-conversion decision procedure, no Church--Rosser theorem, no quotient term equality, no closed subject reduction theorem, and no full consistency theorem.
\end{theorem}
\begin{proof}
Begin with the candidate SN finite socket normal form, Theorem~\ref{thm:metacic-critical-path-candidate-sn-finite-socket-normal-form}. It identifies the consumable candidate-mediated read as exactly the socket-aware rows $S,N,O,U,D,H,C,P,L$ plus the four local L10 face records, with support only from $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next apply confluence-decidability handoff exhaustion, Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It keeps confluence-facing and decidability-facing reads on the displayed packet route and refuses global Church--Rosser, beta-conversion decision, closed subject reduction, and full consistency exports.

Finally use the discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}. It prevents the candidate route from filling the socket coordinate $D$ or promoting candidate evidence into a closed metatheorem.

Combining these three boundaries leaves no extra coordinate for quotient term equality, a global beta-conversion decider, closed subject reduction, or full consistency. Hence every beta-conversion or decidability-facing read mediated by candidates is exhausted by the stated finite socket route and four local face records.
\end{proof}

\begin{theorem}[MetaCIC confluence-decidability candidate SN frontier]
\label{thm:metacic-critical-path-confluence-decidability-candidate-sn-frontier}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
every confluence-facing or decidability-facing read mediated by candidate strong-normalization evidence factors through the finite socket rows $S,N,O,U,D,H,C,P,L$ together with the four local L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The coordinate $D$ remains a separate discharge socket throughout the route. The frontier exports no arbitrary strong-normalization theorem, no Church--Rosser theorem, no beta-conversion decision procedure, no quotient term equality, no selected limit, no countable choice, no closed subject reduction, no full consistency theorem, and no $\RealUp$ completeness claim.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathConfluenceDecidabilityCandidateSNFrontier}
\begin{proof}
Begin with the confluence-decidability handoff exhaustion theorem, Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It confines every confluence-facing or decidability-facing read to the displayed packet rows $S,N,O,U,D,H,C,P,L$ and excludes global Church--Rosser, beta-conversion decision, closed subject reduction, and full consistency exports.

Next add candidate strong-normalization mediation. The candidate-mediated SN boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}, permits only the same packet rows together with the four local L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The finite socket normal form, Theorem~\ref{thm:metacic-critical-path-candidate-sn-finite-socket-normal-form}, repacks exactly this data as the consumable current Phase $\RealUp$ and Completion surface.

Now read the confluence side through Theorem~\ref{thm:metacic-critical-path-confluence-candidate-mediation}. It keeps confluence-facing use on the handoff row $U$, the obstruction and socket rows $O,D$, the structural rows $H,C,P,L$, and the same four local faces, without exporting an arbitrary Church--Rosser theorem.

Finally apply the discharge-refusal and socket-nonescape results, Theorems~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal} and~\ref{thm:metacic-critical-path-candidate-sn-socket-nonescape}. They keep $D$ visible as a separate socket and prevent candidate evidence or the four faces from being read as a discharge, selected limit, countable-choice row, quotient term equality, closed subject reduction, full consistency, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[MetaCIC conditional SN discharge frontier]
\label{thm:metacic-critical-path-conditional-sn-discharge-frontier}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any conditional strong-normalization read mediated by candidates factors through the finite socket normal form over $K$ together with the four local Phase Real faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The discharge socket $D$ remains a separate unmet row and is not converted into closed subject reduction, arbitrary strong normalization, or full consistency.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathConditionalSNDischargeFrontier}
\begin{proof}
Begin with the candidate-mediated SN boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It routes the read through $S,N,O,U,D,H,C,P,L$ and the four local Phase Real faces.

Next apply the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}, and the finite socket normal form, Theorem~\ref{thm:metacic-critical-path-candidate-sn-finite-socket-normal-form}. Together they identify the consumable evidence as the displayed socket-aware packet plus the separate face-local threshold records.

Finally apply the candidate route discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}. It keeps $D$ as the discharge socket coordinate and refuses closed subject reduction and full consistency. Hence conditional SN remains a frontier read through the displayed packet and faces, with $D$ still unmet.
\end{proof}

\begin{theorem}[MetaCIC confluence candidate mediation]
\label{thm:metacic-critical-path-confluence-candidate-mediation}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any confluence-facing read mediated by the candidate route factors through the confluence-decidability handoff row $U$, the obstruction and socket rows $O,D$, the structural rows $H,C,P,L$, and the four local Phase Real faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The read exports no arbitrary Church--Rosser theorem and does not fill the separate discharge socket $D$.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathConfluenceCandidateMediation}
\begin{proof}
Start with the confluence-decidability handoff exhaustion theorem, Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It restricts every confluence-facing downstream read of $U$ to the displayed rows $O,D,H,C,P,L$ together with $S,N,U$.

Attach candidate mediation by applying Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. The only additional evidence available to a candidate-mediated read is the four local Phase Real faces, not a global Church--Rosser theorem or a hidden term-equivalence quotient.

Use Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal} to keep the socket row separate. Since $D$ is not filled by the candidate route and the handoff exhaustion theorem excludes arbitrary Church--Rosser export, the confluence-facing read remains mediated by $K$ and the four displayed faces.
\end{proof}

\begin{theorem}[MetaCIC confluence residual discharge separation]
\label{thm:metacic-critical-path-confluence-residual-discharge}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
a confluence residual row is discharged only when the packet displays a local peak row, a candidate join row, a residual frontier row, a substitution boundary row, a bounded checker row, the obstruction row $O$, and the four L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Candidate-mediated strong-normalization evidence alone cannot fill the discharge socket $D$ or export closed subject reduction, full consistency, a global Church--Rosser theorem, or a beta-conversion decision procedure.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathConfluenceResidualDischarge}
\begin{proof}
Start with the candidate-mediated SN boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It routes every candidate-mediated read through the finite packet rows $S,N,O,U,D,H,C,P,L$ and the four local L10 faces, but it does not add a residual-discharge witness.

Next impose the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. The Phase $\RealUp$ and Completion source surface must expose $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ as separate local records. This audit surface is necessary for a residual confluence read, but it is not the socket discharge.

Now read the confluence and decidability consumer boundary. Theorems~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}, \ref{thm:metacic-critical-path-confluence-candidate-mediation}, and \ref{thm:metacic-critical-path-decidability-fragment-route} keep confluence-facing and bounded-checker reads inside the handoff row, obstruction and socket rows, structural rows, and four displayed faces. Thus a local peak, candidate join, residual frontier, substitution boundary, and bounded checker must be displayed as rows of the same packet route before any residual-discharge claim can be read.

Finally apply the discharge-refusal and socket-separation results. The candidate route discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}, keeps $D$ unmet, while Theorem~\ref{thm:metacic-critical-path-candidate-sn-socket-nonescape} and Theorem~\ref{thm:metacic-critical-path-four-face-socket-separation} prevent the four L10 faces or candidate SN evidence from being absorbed into the discharge socket. Therefore residual confluence discharge requires the displayed residual rows and cannot be supplied by candidate-mediated SN alone.
\end{proof}

\begin{theorem}[MetaCIC decidability fragment route]
\label{thm:metacic-critical-path-decidability-fragment-route}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any bounded decidability-fragment read factors through $K$, the confluence-decidability handoff exhaustion surface, and the four local Phase Real faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The route supplies no global beta-conversion decision procedure, no quotient term equality, no full consistency theorem, and no discharge of the socket row $D$.
\end{theorem}
\begin{proof}
Project the decidability-facing read through Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. The handoff permits only the finite rows $S,N,O,U,D,H,C,P,L$ and excludes global beta-conversion decidability, quotient term equality, closed subject reduction, and full consistency.

Now use the candidate SN finite socket normal form, Theorem~\ref{thm:metacic-critical-path-candidate-sn-finite-socket-normal-form}. A read consumable by the current Phase $\RealUp$ and Completion surface displays the same socket-aware rows together with the four local face records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.

The discharge refusal theorem, Theorem~\ref{thm:metacic-critical-path-candidate-route-discharge-refusal}, keeps $D$ unmet. Therefore the decidability-fragment route is bounded by the displayed packet and face records, and it cannot be promoted to global beta-conversion decidability, quotient equality, full consistency, or a discharged socket.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathDecidabilityFragmentRoute}

\begin{theorem}[MetaCIC neutral-spine decidability handoff]
\label{thm:metacic-critical-path-neutral-spine-decidability-handoff}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
a neutral-spine decidability read may be consumed by the current Phase $\RealUp$ route only after candidate-mediated strong normalization, confluence mediation, and bounded decidability-fragment rows expose the four local L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The handoff supplies no aggregate formalstatus, no bridge row, no quotient stream equality, no selected limit, no choice schedule, and no ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Start with the candidate-mediated strong-normalization boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It allows a neutral-spine read to reach the current route only through the finite packet rows $S,N,O,U,D,H,C,P,L$ and the four local Phase Real faces.

Next add confluence mediation. Theorem~\ref{thm:metacic-critical-path-confluence-candidate-mediation} keeps confluence-facing use on the handoff row $U$, the obstruction and socket rows $O,D$, the structural rows $H,C,P,L$, and the same four displayed faces, while refusing arbitrary Church--Rosser export and any filling of $D$.

Now apply the bounded decidability fragment route, Theorem~\ref{thm:metacic-critical-path-decidability-fragment-route}. Decidability-facing evidence remains bounded by $K$, the confluence-decidability handoff exhaustion surface, and the four local faces; it does not become a global beta-conversion decision procedure or quotient term equality.

Finally read the route through the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. The current Phase $\RealUp$ consumer sees separated $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ records, not an aggregate verification row or bridge credential. The excluded aggregate status, bridge, quotient stream, selected-limit, choice, and ambient-completeness objects are therefore outside the neutral-spine handoff.
\end{proof}

\begin{theorem}[MetaCIC neutral-spine four-face budget]
\label{thm:metacic-critical-path-neutral-spine-four-face-budget}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any neutral-spine read used jointly for candidate-mediated strong
normalization, confluence mediation, and bounded decidability must expose
separate face records for $\DyadicRatCoreUp$, $\StreamNameUp$,
$\RegSeqRatUp$, and $\RealUp$, together with the finite socket rows
$S,N,O,U,D,H,C,P,L$. It exports no aggregate formalstatus, bridge row,
quotient term equality, selected limit, closed subject reduction, full
consistency, or $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathNeutralSpineFourFaceBudget}
\begin{proof}
Start with the candidate-mediated strong-normalization boundary,
Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It
keeps a neutral-spine read on the finite socket rows and on the four local
Phase Real faces.

Add confluence mediation through
Theorem~\ref{thm:metacic-critical-path-confluence-candidate-mediation}. The
confluence-facing use stays on the handoff, obstruction, socket, transport,
replay, provenance, and local naming rows; it does not discharge $D$ or
export closed subject reduction.

Now apply the bounded decidability fragment route,
Theorem~\ref{thm:metacic-critical-path-decidability-fragment-route}, together
with the neutral-spine handoff of
\autoref{thm:metacic-critical-path-neutral-spine-decidability-handoff}. The
decidability read remains bounded by the same packet and cannot become
global beta-conversion decidability or quotient term equality.

Finally impose the four-face audit precondition,
Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}.
It requires $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and
$\RealUp$ to remain separate face records. Therefore the joint read exposes
the displayed socket rows and four faces only, leaving aggregate status,
bridge rows, selected limits, closed subject reduction, full consistency,
and $\RealUp$ completeness outside the budget.
\end{proof}

\begin{theorem}[MetaCIC neutral-spine decidability budget]
\label{thm:metacic-critical-path-neutral-spine-decidability-budget}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any current Phase $\RealUp$ consumer of a neutral-spine decidability row must expose $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ as four separate local faces before it consumes the decidability evidence. The row remains bounded by the finite packet route $S,N,O,U,D,H,C,P,L$ and exports no aggregate formalstatus, bridge row, quotient stream equality, selected limit, global beta-conversion decision procedure, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the neutral-spine handoff of \autoref{thm:metacic-critical-path-neutral-spine-decidability-handoff}. It routes a decidability read through candidate-mediated strong normalization, confluence mediation, and the bounded decidability fragment before it reaches the current Phase $\RealUp$ surface.

Apply the decidability fragment route, \autoref{thm:metacic-critical-path-decidability-fragment-route}. It keeps the bounded checker on the finite packet rows and prevents promotion to a global beta-conversion decision procedure or quotient term equality.

Finally impose the four-face audit precondition, \autoref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. The current consumer must see $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ as separated local records; an aggregate status, bridge row, selected limit, or ambient completeness claim is outside the decidability budget.
\end{proof}
\leanchecked{BEDC.Derived.MetaCICCriticalPathUp.MetaCICCriticalPathNeutralSpineDecidabilityBudget}

\begin{theorem}[MetaCIC residual confluence budget]
\label{thm:metacic-critical-path-residual-confluence-budget}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, any residual-confluence read consumed by the current L10 route must display the same four face records $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before it consumes the confluence row. Candidate-mediated evidence may guide the residual route, but it cannot supply a global Church--Rosser theorem, closed subject reduction, full consistency, socket discharge, quotient term equality, or a Real bridge claim.
\end{theorem}
\begin{proof}
Begin with confluence mediation, \autoref{thm:metacic-critical-path-confluence-candidate-mediation}. It keeps confluence-facing use on the handoff row $U$, obstruction and socket rows $O,D$, structural rows $H,C,P,L$, and the four local faces.

Use the residual discharge separation theorem, \autoref{thm:metacic-critical-path-confluence-residual-discharge}. Residual confluence requires local peak, candidate join, residual frontier, substitution boundary, bounded checker, obstruction, and face rows; candidate-mediated strong normalization alone does not fill the socket.

The four-face audit precondition then keeps the L10 evidence objectwise. Thus a current consumer reads residual confluence only after $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ are separately exposed, and the listed global metatheorems and Real bridge claims remain outside the budget.
\end{proof}

\begin{theorem}[MetaCIC candidate SN discharge budget]
\label{thm:metacic-critical-path-candidate-sn-discharge}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, candidate-mediated strong-normalization evidence may be consumed by the current Phase $\RealUp$ and Completion surface only after the four L10 faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ are displayed separately. The evidence does not discharge the socket row $D$, does not prove closed subject reduction or full consistency, and does not collapse SN, residual confluence, and neutral-spine decidability into one endpoint claim.
\end{theorem}
\begin{proof}
Project the candidate-mediated SN boundary through \autoref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. It permits the SN-facing read only on the finite packet rows and the four Phase Real faces.

Apply the four-face discharge precondition strengthening, \autoref{thm:metacic-critical-path-four-face-discharge-precondition-strengthening}. The socket row $D$ remains visible as an unmet row distinct from $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.

Finally use the socket nonescape and four-face budget results, \autoref{thm:metacic-critical-path-candidate-sn-socket-nonescape} and \autoref{thm:metacic-critical-path-neutral-spine-four-face-budget}. They prevent the candidate route from discharging $D$ or from merging SN, confluence, and decidability into a single endpoint surface. The current consumer therefore receives separated L10 faces and a still-visible socket budget.
\end{proof}

\begin{theorem}[MetaCIC critical-path confluence-decidability exit budget]
\label{thm:metacic-critical-path-confluence-decidability-exit-budget}
For every accepted $\MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any candidate-mediated strong-normalization read that is used both as confluence evidence and as bounded decidability-fragment evidence for the current L10 route must expose four independent phase faces: $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Each face carries its own $\BHist$ support, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The route supplies no aggregate formalstatus, no bridge row, no quotient stream equality, no selected limit, no choice schedule, and no ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Begin with the confluence-decidability handoff exhaustion theorem, Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion}. It confines confluence-facing and decidability-facing reads to the finite packet rows $S,N,O,U,D,H,C,P,L$ and excludes closed subject reduction, full consistency, global beta-conversion decidability, and quotient term equality.

Next apply the candidate-mediated SN boundary, Theorem~\ref{thm:metacic-critical-path-candidate-mediated-sn-boundary}. Candidate mediation can add only the four current Phase Real faces, namely $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, to the displayed packet route.

Now impose the four-face audit precondition, Theorem~\ref{thm:metacic-critical-path-candidate-sn-four-face-audit-precondition}. It requires those four faces to appear as separate local records, each with its own support from $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data rather than as one route-level credential.

Finally combine \autoref{thm:metacic-critical-path-confluence-candidate-mediation} with \autoref{thm:metacic-critical-path-decidability-fragment-route}. The same separated face data must serve both confluence and decidability uses, while aggregate status rows, bridge rows, quotient stream equality, selected limits, choice schedules, and ambient $\RealUp$ completeness remain outside the current L10 exit budget.
\end{proof}
