\begin{theorem}[MetaCIC L10 normalization discharge budget]
\label{thm:metaciccriticalpath-l10-normalization-discharge-budget}
Let
$$
K=(S,N,O,U,D,H,C,P,L)
$$
be an accepted $\MetaCICCriticalPathUp$ packet. Every candidate-mediated strong-normalization, confluence, or decidability admission that is routed toward a discharge socket must first display the four L10 source faces
$$
\DyadicRatCoreUp,\qquad
\StreamNameUp,\qquad
\RegSeqRatUp,\qquad
\RealUp
$$
together with the packet rows $S,N,O,U,D,H,C,P,L$. The discharge socket may then consume only this finite source budget. It receives no closed subject-reduction row, arbitrary strong-normalization theorem, global confluence theorem, beta-conversion decision procedure, quotient term equality, selected limit, host real equality, or $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Begin with the candidate-mediated SN frontier of \autoref{thm:metacic-critical-path-candidate-mediated-sn-frontier}. It already places a candidate-mediated read on $S,N,U,D,H,C,P,L$ and requires the four L10 faces before any confluence-facing or decidability-facing handoff consumes $U$.

Next use the candidate-normalization budget theorem, \autoref{thm:metacic-critical-path-candidate-normalization-budget}. It identifies $S,N,U,H,C,P,L$ plus $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ as the finite normalization surface available to such consumers.

Finally apply discharge-socket induction and socket exhaustion, \autoref{thm:metacic-critical-path-discharge-socket-induction} and \autoref{thm:metacic-critical-path-candidate-normalization-socket-exhaustion}. These keep $O$ and $D$ visible unless a separate closed subject-reduction row is displayed, so the discharge socket consumes only the named L10 budget and none of the refused global claims.
\end{proof}

\begin{theorem}[MetaCIC RegSeqRat candidate-normalization route]
\label{thm:metaciccriticalpath-regseqrat-candidate-normalization-route}
Let
$$
K=(S,N,O,U,D,H,C,P,L)
$$
be an accepted $\MetaCICCriticalPathUp$ packet. Any candidate-normalization route that exposes a regular-rational readback to a confluence-facing or decidability-facing consumer must pass through $\StreamNameUp$ finite windows, $\DyadicRatCoreUp$ tolerance data, and the $\RegSeqRatUp$ readback row before the candidate-normalization handoff $U$ is consumed. The route is therefore a displayed L10 readback route, not a detached normalization oracle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:metacic-critical-path-candidate-mediated-frontier-l10-readback}. It requires every candidate-mediated read of $U$ to expose the four L10 faces before the handoff is passed to a confluence-facing or decidability-facing consumer.

Refine that read with \autoref{thm:metaciccriticalpath-l10-normalization-discharge-budget}. The budget keeps the regular-rational component downstream of the displayed finite windows and dyadic tolerance data, because the accepted discharge surface is the ordered L10 source package rather than an independent oracle.

The consumer-boundary theorem \autoref{thm:metacic-critical-path-confluence-decidability-consumer-boundary} then prevents the handoff from being read as a global confluence theorem or beta-conversion decision procedure. Thus the $\RegSeqRatUp$ row remains part of the visible L10 route.
\end{proof}

\begin{theorem}[MetaCIC Real seal no infinite-reduction handoff]
\label{thm:metaciccriticalpath-real-seal-no-infinite-reduction-handoff}
Let
$$
K=(S,N,O,U,D,H,C,P,L)
$$
be an accepted $\MetaCICCriticalPathUp$ packet. When a candidate-mediated normalization route reaches the $\RealUp$ seal face, the seal records only that the finite L10 readback route has been displayed. It does not certify absence of infinite reduction by itself, fill the discharge socket $D$, erase the obstruction row $O$, or supply closed subject reduction, arbitrary strong normalization, global confluence, beta-conversion decidability, quotient term equality, selected limits, host equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:metaciccriticalpath-l10-normalization-discharge-budget}. It places the $\RealUp$ face after $\DyadicRatCoreUp$, $\StreamNameUp$, and $\RegSeqRatUp$ inside the finite source budget consumed by a discharge socket.

Use \autoref{thm:metacic-critical-path-candidate-normalization-socket-exhaustion}. Even after the candidate-normalization budget and four L10 faces have been consumed, the subject-reduction socket remains unfilled unless a separate closed subject-reduction row is displayed.

Finally apply \autoref{thm:metacic-critical-path-candidate-mediated-frontier-socket-separation}. It keeps $O$ and $D$ visible as rows distinct from the handoff and from the four L10 faces, so the $\RealUp$ seal cannot be reinterpreted as an infinite-reduction exclusion theorem or as any of the refused global metatheoretic claims.
\end{proof}
