¥begin{theorem}[MetaCIC critical-path L10 entry budget synchronization]
¥label{thm:metacic-critical-path-l10-entry-budget-synchronization}
For every current Phase Real or Completion consumer of an accepted $¥MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
entry into the Phase Real route is permitted only after the packet displays the $¥DyadicRatCoreUp$ finite observation budget, the $¥StreamNameUp$ schedule, the $¥RegSeqRatUp$ readback, and the $¥RealUp$ seal rows through finite $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ provenance attached to $K$. The entry surface refuses quotient reals, host equality, trichotomy, open-cover compactness, and completed-real claims.
¥end{theorem}
¥begin{proof}
First expose the packet itself. Theorems‾¥ref{thm:metacic-critical-path-root-unblock-carrier-readiness}, ¥ref{thm:metacic-critical-path-root-unblock-route-readiness}, and ¥ref{thm:metacic-critical-path-root-unblock-consumer-readiness} make $S,N,O,U,D,H,C,P,L$ the displayed carrier, replay, and consumer surface.

Next read the Phase Real dependency budget. Theorems‾¥ref{thm:metacic-critical-path-phase-real-route-budget}, ¥ref{thm:metacic-critical-path-phase-real-normal-form-handoff}, and ¥ref{thm:metacic-critical-path-phase-real-obstruction-ledger-lock} keep the normal-form, obstruction, discharge, continuation, package, and provenance rows visible before a Real-facing handoff.

Finally synchronize the four L10 source rows. Theorems‾¥ref{thm:metacic-critical-path-real-streamname-source-readiness}, ¥ref{thm:metacic-critical-path-regseqrat-readback-readiness}, ¥ref{thm:metacic-critical-path-real-completion-readiness}, ¥ref{thm:metacic-critical-path-dyadicratcore-budget-readiness}, ¥ref{thm:metacic-critical-path-streamname-regseqrat-route-order}, and ¥ref{thm:metacic-critical-path-real-seal-frontier-exactness} identify the dyadic budget, schedule, readback, and seal rows as displayed dependency rows of the same packet. None of these rows carries quotient reals, host equality, trichotomy, open-cover compactness, or a completed-real theorem, so the entry budget is exactly the finite provenance surface described above.
¥end{proof}

¥begin{theorem}[MetaCIC critical-path Real completion frontier filter]
¥label{thm:metacic-critical-path-real-completion-frontier-filter}
For every accepted $¥MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, any Completion-facing claim passed through its Real frontier is admitted only when it is backed by the displayed $¥DyadicRatCoreUp$, $¥StreamNameUp$, $¥RegSeqRatUp$, and $¥RealUp$ L10 source rows of Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization}. Claims that require quotient reals, host equality, trichotomy, open-cover compactness, or completed-real data are filtered out of the packet frontier.
¥end{theorem}
¥begin{proof}
Begin with the synchronized entry budget. Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization} requires the four displayed L10 source rows before the packet can enter the Phase Real route.

The frontier then reads only those rows. Theorem‾¥ref{thm:metacic-critical-path-real-seal-frontier-exactness} identifies the exact seal frontier with the displayed L10 dependency budget, while Theorems‾¥ref{thm:metacic-critical-path-l10-source-cut} and‾¥ref{thm:metacic-critical-path-real-seal-no-completeness-escape} exclude source reads and seal exports outside that budget.

The filter is therefore constructive and finite: a claim survives only by naming the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows attached to $K$. Quotient reals, host equality, trichotomy, open-cover compactness, and completed-real data have no displayed row in that list, so they cannot pass through the frontier.
¥end{proof}

¥begin{theorem}[MetaCIC critical-path current open-phase readiness]
¥label{thm:metacic-critical-path-current-open-phase-readiness}
The current paper-side readiness surface consumed by the Phase Real and Completion route for $¥MetaCICCriticalPathUp$ is the conjunction of the Phase Real dependency budget, the L10 entry budget synchronization of Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization}, and the Real completion frontier filter of Theorem‾¥ref{thm:metacic-critical-path-real-completion-frontier-filter}. This surface is a finite $¥BHist$/$¥hsame$/$¥Cont$/$¥Pkg$/$¥NameCert$ dependency surface and not a claim of quotient reals, host equality, trichotomy, open-cover compactness, or completed-real closure.
¥end{theorem}
¥begin{proof}
The dependency budget supplies the route rows. Theorems‾¥ref{thm:metacic-critical-path-phase-real-route-budget}, ¥ref{thm:metacic-critical-path-phase-real-normal-form-handoff}, and ¥ref{thm:metacic-critical-path-phase-real-obstruction-ledger-lock} expose the finite packet rows consumed by the Phase Real route.

The entry theorem then synchronizes the sources. Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization} requires the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows to be displayed through finite provenance before route entry.

The frontier theorem gives the open-phase filter. Theorem‾¥ref{thm:metacic-critical-path-real-completion-frontier-filter} admits only claims backed by those four displayed source rows and refuses quotient reals, host equality, trichotomy, open-cover compactness, and completed-real data. Together these rows are exactly the current paper-side readiness surface used by the Phase Real and Completion route.
¥end{proof}

¥begin{theorem}[MetaCIC critical-path Phase Real dependency diamond]
¥label{thm:metacic-critical-path-phase-real-dependency-diamond}
For every accepted $¥MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, a public Phase Real or Completion entry is accepted exactly when its route factors through the four displayed source rows attached to $K$: the $¥DyadicRatCoreUp$ finite observation budget, the $¥StreamNameUp$ schedule, the $¥RegSeqRatUp$ readback, and the $¥RealUp$ seal row. The four projections of this factorization recover those source rows and no other public entry row is available. In particular, the diamond exports no quotient stream equality, selected host limit, host equality, trichotomy, open-cover compactness, or completed-real theorem.
¥end{theorem}
¥begin{proof}
Start from the current open-phase surface. Theorem‾¥ref{thm:metacic-critical-path-current-open-phase-readiness} says that a Phase Real or Completion consumer sees the Phase Real dependency budget together with the synchronized L10 entry surface and the Real completion frontier filter.

The entry side supplies the four displayed sources. Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization} requires the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows before public entry, while Theorem‾¥ref{thm:metacic-critical-path-real-completion-frontier-filter} admits only claims backed by those rows at the Completion frontier.

The projections are forced by the readiness and order rows. Theorems‾¥ref{thm:metacic-critical-path-real-streamname-source-readiness}, ¥ref{thm:metacic-critical-path-regseqrat-readback-readiness}, ¥ref{thm:metacic-critical-path-real-completion-readiness}, and ¥ref{thm:metacic-critical-path-dyadicratcore-budget-readiness} identify the four sources as rows of the same packet $K$.

Finally use the route-order and seal-frontier exactness theorems. Theorems‾¥ref{thm:metacic-critical-path-streamname-regseqrat-route-order} and‾¥ref{thm:metacic-critical-path-real-seal-frontier-exactness} place those rows in the displayed diamond and exclude off-budget exits. Hence the public entry route factors through exactly the four source rows, and the excluded completion or host principles have no exported coordinate.
¥end{proof}

¥begin{theorem}[MetaCIC critical-path four source-owner noncollapse]
¥label{thm:metacic-critical-path-four-source-owner-noncollapse}
For every accepted $¥MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, any Phase Real or Completion public entry accepted through the dependency diamond of Theorem‾¥ref{thm:metacic-critical-path-phase-real-dependency-diamond} retains four separate source-owner records: the $¥DyadicRatCoreUp$ finite observation budget owner, the $¥StreamNameUp$ schedule owner, the $¥RegSeqRatUp$ readback owner, and the $¥RealUp$ seal owner. Identifying two of these owners, replacing one owner by an aggregate route-status token, or substituting quotient stream equality, selected host limit, host equality, trichotomy, open-cover compactness, closed consistency, or completed-real data places the entry outside the accepted finite route.
¥end{theorem}
¥begin{proof}
Start with the finite surface. Theorem‾¥ref{thm:metacic-critical-path-current-open-phase-readiness} says that the Phase Real and Completion consumer sees only the displayed $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ rows attached to the packet $K$.

The entry budget then fixes the owner list. Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization} requires the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows as four displayed sources before the route is entered.

The frontier removes every substitute. Theorem‾¥ref{thm:metacic-critical-path-real-completion-frontier-filter} rejects claims that need quotient stream equality, selected host limits, host equality, trichotomy, open-cover compactness, closed consistency, or completed-real data rather than one of the displayed source rows.

Finally apply the diamond. Theorem‾¥ref{thm:metacic-critical-path-phase-real-dependency-diamond} recovers exactly the four projections from an accepted public entry. If two owners were identified, or if an aggregate route-status token replaced one owner, one of those projections would no longer recover its named source row. Such an entry therefore lacks the required four-coordinate factorization and is not an accepted finite route.
¥end{proof}

¥begin{theorem}[MetaCIC critical-path L10 prefix dependency induction]
¥label{thm:metacic-critical-path-l10-prefix-dependency-induction}
For every accepted $¥MetaCICCriticalPathUp$ packet
$$
K=(S,N,O,U,D,H,C,P,L),
$$
any Phase Real or Completion route admitted by Theorem‾¥ref{thm:metacic-critical-path-phase-real-dependency-diamond} has four finite route prefixes: the $¥DyadicRatCoreUp$ budget prefix, the $¥StreamNameUp$ schedule prefix, the $¥RegSeqRatUp$ readback prefix, and the $¥RealUp$ seal prefix. These prefixes occur in that source order, each factors through the displayed packet rows of Theorems‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization}, ¥ref{thm:metacic-critical-path-real-completion-frontier-filter}, ¥ref{thm:metacic-critical-path-phase-real-dependency-diamond}, and‾¥ref{thm:metacic-critical-path-four-source-owner-noncollapse}, and each preserves the obstruction, discharge, host, continuation, package, and ledger rows $O,D,H,C,P,L$. No prefix may be replaced by quotient stream equality, selected host limits, host equality, trichotomy, open-cover compactness, closed subject reduction, full consistency, or completed-real data.
¥end{theorem}
¥begin{proof}
Begin with the entry requirement. Theorem‾¥ref{thm:metacic-critical-path-l10-entry-budget-synchronization} admits a Phase Real route only after the packet displays the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows through finite $¥BHist$, $¥hsame$, $¥Cont$, $¥Pkg$, and $¥NameCert$ provenance.

The frontier supplies the exclusion step. Theorem‾¥ref{thm:metacic-critical-path-real-completion-frontier-filter} says that Completion-facing claims survive only when backed by those displayed rows, so the forbidden substitutes have no route coordinate to occupy.

The diamond gives the constructive prefix split. Theorem‾¥ref{thm:metacic-critical-path-phase-real-dependency-diamond} recovers the four projections from an accepted entry, hence the route can be read as the ordered finite prefix chain from budget to schedule to readback to seal.

Finally keep the owners and packet rows fixed. Theorem‾¥ref{thm:metacic-critical-path-four-source-owner-noncollapse} prevents any two source owners from collapsing and rules out aggregate route-status replacements. Therefore each prefix remains attached to its own source row while carrying forward the common obstruction, discharge, host, continuation, package, and ledger rows $O,D,H,C,P,L$.
¥end{proof}
