\begin{theorem}[MetaCIC critical-path L10 four-object exit certificate]
\label{thm:metacic-critical-path-l10-four-object-exit-certificate}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, the current Phase Real and Completion exit surface is reached exactly by displaying four finite source rows attached to $K$: the $\DyadicRatCoreUp$ finite dyadic budget, the $\StreamNameUp$ finite schedule row, the $\RegSeqRatUp$ regular-rational readback row, and the $\RealUp$ terminal seal row. Each displayed row is carried through finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance, as synchronized by Theorem~\ref{thm:metacic-critical-path-l10-entry-budget-synchronization}, filtered by Theorem~\ref{thm:metacic-critical-path-real-completion-frontier-filter}, arranged by Theorem~\ref{thm:metacic-critical-path-phase-real-dependency-diamond}, and kept source-owner separated by Theorem~\ref{thm:metacic-critical-path-four-source-owner-noncollapse}. No additional exit coordinate is supplied by quotient stream equality, selected host limits, host real equality, trichotomy, open-cover compactness, countable choice, or completed-real closure.
\end{theorem}
\begin{proof}
First take the synchronized L10 entry surface. Theorem~\ref{thm:metacic-critical-path-l10-entry-budget-synchronization} requires the dyadic budget, StreamName schedule, RegSeqRat readback, and Real seal rows to be displayed through finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance before a Phase Real or Completion consumer can enter the route.

Next pass to the Completion-facing frontier. Theorem~\ref{thm:metacic-critical-path-real-completion-frontier-filter} admits only claims backed by those four displayed rows, so every accepted exit certificate still reads from the same finite packet surface rather than from quotient stream equality, selected host limits, host real equality, trichotomy, open-cover compactness, countable choice, or completed-real data.

The dependency shape is then fixed by the diamond. Theorem~\ref{thm:metacic-critical-path-phase-real-dependency-diamond} says that a public Phase Real or Completion entry factors through exactly the four displayed source rows and recovers no other public entry row.

Finally retain the four owners separately. Theorem~\ref{thm:metacic-critical-path-four-source-owner-noncollapse} refuses any collapse of the dyadic budget owner, StreamName schedule owner, RegSeqRat readback owner, and Real seal owner into an aggregate route token. The four-object certificate is therefore precisely the current finite exit surface, and every listed host, choice, compactness, quotient, or completed-real principle remains outside the accepted packet route.
\end{proof}

\begin{theorem}[MetaCIC critical-path L10 status bridge obligation]
\label{thm:metacic-critical-path-l10-status-bridge-obligation}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, any use of Theorem~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate} as Phase Real and Completion exit evidence must pass through the Real L10 objectwise audit pullback of Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback}. The $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces each contribute their own local closurestatus, formalstatus, leantarget, and bridgestatus rows, read from their local closurestatus blocks and not from an aggregate route credential.

Consequently the MetaCIC four-object certificate can be consumed only through the objectwise status discipline of Theorem~\ref{thm:real-l10-face-status-noncollapse} and Theorem~\ref{thm:real-l10-phase-exit-criterion-objectwise}. It supplies no quotient stream equality, no selected host limit, no aggregate bridge row, and no $\RealUp$ completeness claim beyond the four local face records.
\end{theorem}
\begin{proof}
First read the MetaCIC certificate itself. Theorem~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate} displays exactly four finite source rows attached to $K$: the dyadic budget, StreamName schedule, RegSeqRat readback, and Real terminal seal rows.

Next apply the Real L10 audit pullback. Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback} replaces any aggregate reading of that displayed route by the product of the four local face records. Each face is therefore read through its own closurestatus, formalstatus, leantarget, and bridgestatus entries.

Now use Theorem~\ref{thm:real-l10-face-status-noncollapse}. The four local face reports remain separate and cannot be fused into a new formalstatus token, route-level bridge row, or $\RealUp$ completeness report.

Finally apply Theorem~\ref{thm:real-l10-phase-exit-criterion-objectwise}. A Phase Real and Completion exit is accepted only when the four objectwise face records are presented, so quotient stream equality, selected host limits, aggregate bridge rows, and completed-real closure remain outside the MetaCIC L10 evidence.
\end{proof}

\begin{theorem}[MetaCIC Phase Real four-face obligation surface]
\label{thm:metacic-critical-path-phase-real-four-face-obligation-surface}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, a Phase Real exit accepted through $K$ is obligated to present four separate object rows: a $\DyadicRatCoreUp$ finite-budget row, a $\StreamNameUp$ schedule row, a $\RegSeqRatUp$ readback row, and a $\RealUp$ seal row. The rows are read as distinct $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surfaces, and no one of the four may be replaced by an aggregate MetaCIC route token or by a downstream Completion credential.
\end{theorem}
\begin{proof}
Start with the four-object exit certificate of Theorem~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate}. It already identifies the accepted exit surface over $K$ with the dyadic budget, StreamName schedule, RegSeqRat readback, and Real terminal seal rows, each carried by finite packet provenance.

Use the status bridge obligation of Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation} to route that certificate through the Real L10 objectwise audit pullback. Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback} then forces the displayed route to be read as the product of the four local face records, rather than as a single MetaCIC status row.

Finally apply Theorem~\ref{thm:real-l10-phase-exit-criterion-objectwise}. Since the Phase Real exit criterion accepts only the objectwise presentation, every accepted exit through $K$ must expose the four named obligation rows separately. The resulting surface is exactly the root-unblock obligation surface for the current Phase Real route.
\end{proof}

\begin{theorem}[MetaCIC Phase Real status-product readiness]
\label{thm:metacic-critical-path-phase-real-status-product-readiness}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, the Phase Real exit evidence through $K$ is ready for downstream consumption only when the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces each supply their own local closurestatus, formalstatus, leantarget, and bridgestatus rows. These four reports are read independently from the local face chapters and are not inferred from the aggregate MetaCIC four-object certificate.
\end{theorem}
\begin{proof}
First read the accepted packet through Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation}. It states that any use of the MetaCIC four-object certificate as Phase Real and Completion exit evidence must pass through the Real L10 objectwise audit pullback.

The audit pullback of Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback} supplies the product reading: each of the four faces contributes its own closurestatus, formalstatus, leantarget, and bridgestatus row. This gives readiness only after all four local records have been displayed.

The noncollapse clauses now rule out aggregate substitution. Theorem~\ref{thm:real-l10-face-status-noncollapse} prevents a fused formalstatus or route-level bridge row, and Theorem~\ref{thm:real-l10-face-leantarget-noncollapse} keeps the leantarget rows local to their four face chapters. Thus downstream consumers receive a four-entry status product, not a single MetaCIC route credential.
\end{proof}

\begin{theorem}[MetaCIC Phase Real exit refusal boundary]
\label{thm:metacic-critical-path-phase-real-exit-refusal-boundary}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, the Phase Real exit through $K$ refuses quotient stream equality, selected host limits, host equality, trichotomy, open-cover compactness, countable choice, and completed-real closure. The only accepted exit data are the four finite object rows of Theorem~\ref{thm:metacic-critical-path-phase-real-four-face-obligation-surface} together with their local status-product rows of Theorem~\ref{thm:metacic-critical-path-phase-real-status-product-readiness}.
\end{theorem}
\begin{proof}
Begin with Theorem~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate}. Its final exclusion list already keeps quotient stream equality, selected host limits, host real equality, trichotomy, open-cover compactness, countable choice, and completed-real closure outside the four-object exit certificate.

Next use Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation}. It says that the certificate can be consumed only through the Real L10 objectwise status discipline, and it supplies no quotient stream equality, no selected host limit, no aggregate bridge row, and no $\RealUp$ completeness claim beyond the four local face records.

The Real L10 audit theorems make the refusal stable under downstream reading. Theorem~\ref{thm:real-l10-face-status-noncollapse} prevents the missing coordinates from reappearing as a fused status row, while Theorem~\ref{thm:real-l10-phase-exit-criterion-objectwise} accepts the exit only through the four objectwise face records.

Combining the four-face obligation surface with the status-product readiness theorem therefore leaves no admissible entry point for quotient equality, selected limits, host equality, trichotomy, open-cover compactness, countable choice, or completed-real closure. These principles remain outside the accepted Phase Real exit boundary through $K$.
\end{proof}

\begin{theorem}[MetaCIC critical-path four-face deficiency refusal]
\label{thm:metacic-critical-path-four-face-deficiency-refusal}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, suppose that at least one of the four faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ fails to provide the local closurestatus, formalstatus, leantarget, and bridgestatus row required by Theorem~\ref{thm:real-l10-phase-exit-criterion-objectwise}. Then the MetaCIC four-object route through $K$ cannot be consumed as Phase Real and Completion exit evidence.

In particular, the missing face cannot be replaced by an aggregate formalstatus row, an aggregate bridge row, quotient stream equality, a selected host limit, countable choice, or a $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
First route the accepted packet through the MetaCIC status bridge. Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation} sends every use of the four-object certificate to the Real L10 objectwise audit pullback, and Theorem~\ref{thm:metacic-critical-path-phase-real-status-product-readiness} says that downstream readiness is obtained only from the four local face rows.

Now apply the Real-side blocker. Theorem~\ref{thm:real-l10-face-audit-minimum-blocker} states that a deficient face in the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ product prevents the current Phase Real and Completion exit criterion from being satisfied. Since the MetaCIC route is consumed only through that product, the deficient face blocks consumption of the route as exit evidence.

Finally use the noncollapse theorems to rule out substitutes. Theorem~\ref{thm:real-l10-face-status-noncollapse} prevents an aggregate formalstatus token, aggregate bridge row, quotient stream, selected limit, countable-choice coordinate, or $\RealUp$ completeness report from filling the missing local status coordinate. Theorem~\ref{thm:real-l10-face-leantarget-noncollapse} keeps leantarget and bridgestatus rows local to their four face chapters. Thus the contrapositive obstruction is route-level: without all four local face records, the MetaCIC four-object route supplies no admissible Phase Real and Completion exit evidence.
\end{proof}

\begin{theorem}[MetaCIC critical-path L10 face target locality]
\label{thm:metacic-critical-path-l10-face-leantarget-locality}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, each Phase Real face $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ must supply its own local leantarget and bridgestatus row when the packet is consumed as Phase Real and Completion exit evidence. These rows are read through the Real L10 objectwise audit pullback of Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback}; no aggregate MetaCIC route target, route-level bridge row, quotient stream equality, selected host limit, countable-choice coordinate, or $\RealUp$ completeness claim can replace any one of the four local rows.
\end{theorem}
\begin{proof}
Start from the status bridge obligation. Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation} says that any use of the accepted MetaCIC four-object certificate as Phase Real and Completion exit evidence must pass through the Real L10 objectwise audit pullback.

The pullback then fixes the reading of the target and bridge rows. By Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback}, the exit evidence is inspected as the product of the four local face records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, not as a single route credential.

Apply the two Real-side noncollapse clauses. Theorem~\ref{thm:real-l10-face-leantarget-noncollapse} keeps each leantarget row attached to its own face chapter, and Theorem~\ref{thm:real-l10-face-status-noncollapse} prevents a fused status or bridge row from replacing that face-local audit record.

Finally use Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal}. If any face-local leantarget or bridgestatus row is missing, the missing coordinate cannot be supplied by an aggregate MetaCIC route target, route-level bridge row, quotient stream equality, selected host limit, countable-choice coordinate, or $\RealUp$ completeness claim. Thus the target and bridge coordinates are objectwise obligations for the four displayed faces.
\end{proof}

\begin{theorem}[MetaCIC Phase Real audit-clean floor]
\label{thm:metacic-critical-path-phase-real-audit-clean-floor}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, the packet can be consumed as Phase Real and Completion exit evidence only when the four faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ are each read through their own local closurestatus record at least $\scopedClosure$ and their own local formalstatus record at least $\auditCleanV$. The comparison is made face by face through the Real L10 audit pullback of Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback} and the objectwise exit threshold equivalence of Theorem~\ref{thm:real-l10-objectwise-exit-threshold-equivalence}.

No aggregate route status, aggregate bridge row, quotient stream equality, selected host limit, countable-choice coordinate, or $\RealUp$ completeness claim can substitute for any one of those four local closure and audit-clean verification records.
\end{theorem}
\begin{proof}
Start from the face-local reading. Theorem~\ref{thm:metacic-critical-path-l10-face-leantarget-locality} says that the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ target and bridge rows are local obligations whenever $K$ is consumed as Phase Real and Completion exit evidence.

Apply the Real L10 pullback. Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback} reads the accepted route as the product of the four local face records, not as a single MetaCIC route status. Theorem~\ref{thm:real-l10-objectwise-exit-threshold-equivalence} identifies the current exit threshold with local theory-closure rows and local audit-clean verification rows on exactly those four faces.

It remains to exclude substitutes. Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal} blocks consumption when any required face-local record is absent. The same refusal rules out aggregate route status, aggregate bridge rows, quotient stream equality, selected host limits, countable choice, and $\RealUp$ completeness as replacements for the missing face-local closure or audit-clean record.
\end{proof}

\begin{theorem}[MetaCIC four-face audit floor]
\label{thm:metacic-critical-path-four-face-audit-floor}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$, the complete MetaCIC consumer-side audit floor for the current Phase Real route is the conjunction of the status bridge obligation of Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation}, the audit-clean floor of Theorem~\ref{thm:metacic-critical-path-phase-real-audit-clean-floor}, and the four-face deficiency refusal of Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal}. A downstream consumer may therefore accept the route only by displaying all four local face records at the stated closure and verification threshold, with the listed deficiencies still refused.
\end{theorem}
\begin{proof}
First apply the status bridge obligation. Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation} sends every use of the accepted MetaCIC four-object certificate to the Real L10 objectwise audit pullback and prevents the consumer from reading a route-level credential in place of local face data.

Next apply Theorem~\ref{thm:metacic-critical-path-phase-real-audit-clean-floor}. It raises the local status product to the current Phase Real threshold: each of $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ must contribute its own closurestatus record at least $\scopedClosure$ and its own formalstatus record at least $\auditCleanV$.

Finally apply Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal}. If any one of the four face records is missing or below the required local threshold, the route cannot be consumed as Phase Real and Completion exit evidence. Thus the three cited theorems form the complete consumer-side audit floor for the current MetaCIC route.
\end{proof}

\begin{theorem}[MetaCIC Phase Real consumer minimality]
\label{thm:metacic-critical-path-phase-real-consumer-minimality}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$ consumed as Phase Real and Completion exit evidence, every downstream consumer must retain all four Phase Real face rows $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows attached to those faces. Deleting or replacing any one of those face rows or support rows prevents $K$ from being consumed as current phase exit evidence.

No aggregate MetaCIC route token, aggregate formalstatus row, aggregate bridge row, quotient stream equality, selected host limit, countable-choice coordinate, metric-completeness row, or $\RealUp$ completeness claim can repair the deletion.
\end{theorem}
\begin{proof}
First route the consumer through the status bridge. Theorem~\ref{thm:metacic-critical-path-l10-status-bridge-obligation} says that every use of the MetaCIC four-object certificate as Phase Real and Completion exit evidence passes through the Real L10 objectwise audit pullback of Theorem~\ref{thm:real-l10-current-phase-exit-audit-pullback}.

The audit floor then fixes the local threshold. Theorem~\ref{thm:metacic-critical-path-four-face-audit-floor} combines the status bridge, Theorem~\ref{thm:metacic-critical-path-phase-real-audit-clean-floor}, and the four-face deficiency refusal into the consumer-side audit floor. Theorem~\ref{thm:real-l10-objectwise-exit-threshold-equivalence} reads that floor objectwise, so every local face record is part of the accepted exit threshold.

Now remove one displayed face row or one displayed support row. If the removed row belongs to the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ face product, Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal} blocks consumption of the route as Phase Real and Completion exit evidence.

If the consumer proposes an aggregate substitute, the Real L10 noncollapse clauses reject it. Theorem~\ref{thm:real-l10-face-status-noncollapse} prevents aggregate status, bridge, quotient, selected-limit, countable-choice, metric-completeness, and $\RealUp$ completeness data from filling a missing face coordinate.

It remains to account for the finite support rows. The four-object certificate of Theorem~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate} carries the four faces through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface, and Theorem~\ref{thm:metacic-critical-path-phase-real-four-face-obligation-surface} makes that surface part of the Phase Real obligation. Thus deleting or replacing any displayed support row removes the finite route by which the objectwise audit pullback reads the face, and no aggregate credential can repair the loss.
\end{proof}

\begin{theorem}[MetaCIC L10 four-face consumer threshold]
\label{thm:metacic-critical-path-l10-four-face-consumer-threshold}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$ consumed as current Phase Real and Completion exit evidence, the consumer threshold is the facewise conjunction of the four local records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. Each face must contribute its own local closurestatus row at the scoped object boundary and its own audit-clean formalstatus row, together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows attached to that face.

The threshold is not satisfied by the aggregate MetaCIC route token, by a route-level formalstatus row, by a route-level bridge row, by quotient stream equality, by selected host limits, by countable choice, or by an ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Start with Theorem~\ref{thm:metacic-critical-path-phase-real-consumer-minimality}. It says that every downstream consumer must retain all four Phase Real face rows and the finite support rows attached to those faces.

Apply Theorem~\ref{thm:metacic-critical-path-four-face-audit-floor}. The consumer-side audit floor is obtained only by displaying all four local face records at the stated closure and verification threshold. In particular, each of $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ must supply its own closurestatus and audit-clean formalstatus data through the Real L10 objectwise audit pullback.

Finally use Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal}. If any one face lacks the required local record, the accepted packet cannot be consumed as Phase Real and Completion exit evidence. The same refusal excludes aggregate MetaCIC route tokens, route-level status, route-level bridge data, quotient stream equality, selected host limits, countable choice, and ambient Real completeness as replacements for the missing facewise threshold row.
\end{proof}

\begin{theorem}[MetaCIC L10 four-face bridge deferral]
\label{thm:metacic-critical-path-l10-four-face-bridge-deferral}
For every accepted $\MetaCICCriticalPathUp$ packet $K=(S,N,O,U,D,H,C,P,L)$ consumed as current Phase Real and Completion exit evidence, bridge closure is deferred face by face to the local $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ records. The aggregate four-object route may expose the finite exit surface and the consumer threshold of Theorem~\ref{thm:metacic-critical-path-l10-four-face-consumer-threshold}, but it cannot supply a bridgeChecked row for any face whose local closurestatus block has not supplied that bridge record.

Thus a bridge consumer must inspect the four local bridgestatus rows separately. No aggregate MetaCIC route token, route-level bridge row, quotient stream equality, selected host limit, countable-choice coordinate, metric-completeness row, or ambient $\RealUp$ completeness claim can close a missing face bridge.
\end{theorem}
\begin{proof}
First read the local target and bridge rows. Theorem~\ref{thm:metacic-critical-path-l10-face-leantarget-locality} makes each of the four Phase Real faces responsible for its own leantarget and bridgestatus row whenever $K$ is consumed as Phase Real and Completion exit evidence.

Next apply the consumer threshold theorem. Theorem~\ref{thm:metacic-critical-path-l10-four-face-consumer-threshold} gives the current audit-clean threshold as a facewise product, not as an aggregate MetaCIC status. Therefore the four-object route can expose the threshold only by presenting the local face records.

Now use Theorem~\ref{thm:real-l10-face-leantarget-noncollapse} and Theorem~\ref{thm:real-l10-face-status-noncollapse}. These noncollapse clauses keep leantarget, formalstatus, and bridge rows attached to their own face chapters and prevent a fused route credential from replacing any one of them.

Finally apply Theorem~\ref{thm:metacic-critical-path-four-face-deficiency-refusal}. A missing local bridge record is a deficient face record for bridge consumption, and no aggregate MetaCIC route token, route-level bridge row, quotient stream equality, selected host limit, countable choice, metric-completeness row, or ambient Real completeness claim can repair it. Bridge closure is therefore postponed to the four local face records separately.
\end{proof}
