\begin{theorem}[MetaCIC critical-path split obligation surface]
\label{thm:metacic-critical-path-split-obligation-surface}
Every critical-path consumer that claims a $\MetaCICCriticalPathUp$ handoff must expose, before the claim is consumed, the candidate-mediated strong-normalisation row, finite-observation confluence row, closure-trace row, residual substitution boundary row, normalization-frontier row, and subject-reduction discharge row. These six rows are read as displayed packet coordinates tied to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\MetaCICCriticalPathUp}$ surface; no consumer may replace them by a host scheduler edge, a hidden theorem export, a global Church--Rosser assertion, or an unstated subject-reduction theorem.
\end{theorem}
\begin{proof}
Project the accepted critical-path packet to the rows already named by the MetaCIC carrier and its downstream child surfaces. The candidate-mediated strong-normalisation row supplies the normalization source, and the normalization-frontier row records the finite point at which that source may be inspected.

Read the confluence and closure rows next. Finite-observation confluence is available only as a displayed observation row, while the closure trace records the finite replay route rather than a global confluence theorem.

The residual substitution boundary and subject-reduction discharge rows are then kept visible as boundaries. They can be transported and replayed through $\hsame$ and $\Cont$, but they cannot be collapsed into a supplied subject-reduction theorem.

Finally the structural rows source and name the same six-row surface through $\Pkg$ and $\NameCert_{\MetaCICCriticalPathUp}$. Since host scheduler edges, hidden theorem exports, global Church--Rosser, and unstated subject reduction are not packet coordinates, every critical-path handoff consumer must expose the six displayed obligation rows before claiming the handoff.
\end{proof}
