\begin{theorem}[MetaCICCriticalPath Phase Real source obligations]
\label{thm:metacic-critical-path-phase-real-source-obligations}
Every Phase Real $\MetaCICCriticalPathUp$ read must expose the four source
rows $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$
before any discharge socket, confluence-decidability handoff, obstruction
boundary, or downstream readiness boundary is consumed. The read is therefore
budgeted by the displayed packet rows, finite observation budget, source
schedule, regular-rational readback, Real seal, $\BHist$ history rows,
$\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$
rows; it cannot start from a socket row, a confluence theorem, a decidability
procedure, closed subject reduction, full consistency, quotient stream
equality, a selected limit, or host equality.
\end{theorem}
\begin{proof}
First read the Phase Real dependency budget. Theorems~\ref{thm:metacic-critical-path-dyadicratcore-budget-readiness}, \ref{thm:metacic-critical-path-streamname-regseqrat-route-order}, and \ref{thm:metacic-critical-path-real-seal-frontier-exactness} put the dyadic finite-observation row before the StreamName schedule, the RegSeqRat readback, and the Real seal.

Next use the four-object exit certificate. Theorems~\ref{thm:metacic-critical-path-l10-four-object-exit-certificate}, \ref{thm:metacic-critical-path-phase-real-four-face-obligation-surface}, and \ref{thm:metacic-critical-path-phase-real-exit-refusal-boundary} identify the four Phase Real source faces and refuse external completion, closed consistency, and off-ledger theorem rows.

Then route the read through the open source ledger. Definition~\ref{def:metacic-critical-path-open-phase-source-ledger} lists the packet rows and the four Phase Real source rows, while Theorems~\ref{thm:metacic-critical-path-open-phase-source-closure}, \ref{thm:metacic-critical-path-open-phase-consumer-totality}, and \ref{thm:metacic-critical-path-open-phase-exact-boundary-handoff} keep those rows as the whole visible source surface.

Finally attach the confluence-decidability budget. Theorem~\ref{thm:metaciccriticalpath-confluence-decidability-budget} and Theorem~\ref{thm:metacic-critical-path-confluence-decidability-handoff-exhaustion} allow confluence-facing and decidability-facing consumers only after the ledger and socket rows have been displayed. This matches the existing Lean-facing packet names for discharge socket coverage, transport row stability, kernel frontier exposure, and downstream readiness boundary: each consumes displayed BEDC rows rather than supplying a hidden source before $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ have been exposed.
\end{proof}
