\subsection{Multi-history physics route}
\label{subsec:philosophy-programme-multihist-physics}

\begin{definition}[Multi-history physics chain]
\label{def:philosophy-programme-multihist-physics-chain}
The multi-history physics route proceeds through naming certificates
for multi-history configuration, cross-history causal dependence,
maximum causal rate, Lorentz-style geometry, curved spacetime as
Lorentz data with gluing, and quantum-state structure as a
multi-history superposition interface.
\end{definition}
\concretizedIn{ch:concrete-instances-causal-intervention-namecert}{finite causal intervention NameCert}

\concretizedIn{ch:concrete-instances-crosshistorycausaldependence-namecert}{Multi-history causal dependence is realized as a finite no-global-frame causal-route packet.}

\concretizedIn{ch:concrete-instances-multi-history-physics-route-namecert}{The multi-history physics route is realized as a composite finite NameCert packet over relational physics, physical-law bridge, scientific-model bridge, and quantum-state rows with explicit falsification boundaries.}

\begin{definition}[Physics falsification surface]
\label{def:philosophy-programme-physics-falsification}
Each physical step carries a falsification surface. Multi-history
configuration fails if it requires a global frame. Cross-history causal
dependence fails if it cannot be expressed as a stable predicate.
Maximum causal rate fails if it requires choice. Lorentz-style
geometry fails if its distance shape is not symmetric or invariant.
Curved spacetime fails if gluing cannot be constructive. Quantum-state
structure fails if the superposition predicate forces propositional
extensionality.
\end{definition}

\concretizedIn{ch:concrete-instances-physics-falsification-surface-namecert}{Physics falsification surfaces are realized as finite physical-route, law, empirical-persistence, countermodel, bridge-audit, axiom-purity, typed-gap, transport, provenance, and NameCert rows.}

\begin{theorem}[Physics failure is structural]
\label{thm:philosophy-programme-physics-failure-structural}
If the multi-history physics route cannot remain inside the
axiom-purity gate, the failure point is itself a BEDC structural
result.
\end{theorem}
\begin{proof}
The route asks whether physical relational semantics can be closed
without choice, quotient collapse, or propositional extensionality. A
failure identifies the first schema where distinction, history,
continuation, and certificate discipline are insufficient. That
location is structural information.
\end{proof}

\begin{corollary}[Physics route does not presume success]
\label{cor:philosophy-programme-physics-not-presumed}
The physics route should be written as well-posed interface,
falsification surface, and axiom-purity test, not as a completed
derivation of relativity or quantum mechanics.
\end{corollary}
\begin{proof}
The route currently licenses a structural form and dependency chain.
It does not supply empirical values or completed physical theories.
\end{proof}

\subsection{Research programme synthesis}
\label{subsec:philosophy-programme-synthesis}

\begin{theorem}[Research programme synthesis]
\label{thm:philosophy-programme-synthesis}
The BEDC research programme is layered, certified, strength-marked,
phase-governed, failure-aware, boundary-honest, audit-facing, and
physics-aware.
\end{theorem}
\begin{proof}
The programme is layered by the L0--L14 dependency route. It is
certified because each mature name requires a naming certificate. It is
strength-marked by the seed, paper, machine-checked, and conservative
bridge gradient. It is phase-governed because only the current open
phase is sanctioned. It is failure-aware because failure certificates
block promotion while identifying missing fields. It is
boundary-honest because cannot-claim entries record current refusals.
It is audit-facing because reports must state checker, command,
checked names, pending statements, host leakage, and axiom status. It
is physics-aware because multi-history physics is treated as a roadmap
with falsification surfaces rather than a completed theory.
\end{proof}

\begin{corollary}[After philosophy]
\label{cor:philosophy-programme-after-philosophy}
After the philosophical synthesis, the priority is not to add more
interpretive prose but to turn philosophical concepts into writing
items, gap reports, tradition maps, formal targets, lowest-layer
naming certificates, failure certificates, and cannot-claim entries.
\end{corollary}
\begin{proof}
The interpretive frame is already present. Progress comes from moving
readings into certificate and audit discipline at the lowest open
layer.
\end{proof}

\begin{corollary}[Execution maxim]
\label{cor:philosophy-programme-execution-maxim}
Do not extend BEDC by assertion. Extend it by certificate.
\end{corollary}

\subsection{Programme summary}
\label{subsec:philosophy-programme-summary}

\begin{definition}[Programme compression]
\label{def:philosophy-programme-compression}
The future of BEDC is not the claim that mature objects are already
possessed. It is the progressive discharge of naming certificates,
ledgers, stability obligations, bridges, failure surfaces, and audit
reports by which each name proves its right to be used.
\end{definition}
