
\chapter{Proof Standing Manifest v1.3}

This part is the v1.3 proof-standing increment. It does not introduce new large derived interfaces. Its purpose is to make the finite kernel stand by organizing the existing kernel into proof blocks, sharpening theorem dependencies, and recording the exact paper-proof status of each finite-kernel target.

\begin{principle}[Proof-first increment]
After the finite kernel target is frozen, the next live work is not horizontal expansion but vertical proof consolidation. In this increment, a statement is advanced only when it is placed in one of the following statuses:
\[
\mathsf{PaperProof},\qquad \mathsf{ProofSketch},\qquad \mathsf{ContractOnly},\qquad \mathsf{Deferred}.
\]
The first status means that this volume gives a mathematical proof at the object-theory specification level. It does not mean machine verification unless a separate verification log states so.
\end{principle}

\begin{definition}[Proof-standing layer]
The proof-standing layer is the active refinement layer following the frozen finite kernel and the v10.1 proof target. Its scope is restricted to:
\begin{enumerate}
  \item internal sameness of marks and histories;
  \item relationized extension and continuation;
  \item signature generation under asking policies;
  \item signature sameness;
  \item package/gap coverage and separation;
  \item composite ledger coverage;
  \item proof obligations attached to typed naming certificates.
\end{enumerate}
It explicitly excludes full real-like, circle-like, fold-like, and completed arithmetic theories.
\end{definition}

\begin{remark}[Current proof status]
The statements in this part are paper-level proof standing statements. They are designed to be translated into the external proof-assistant contract. The current master project still records machine verification as pending.
\end{remark}
