
\chapter{Package and Gap Proof Spine}
\label{ch:proof-standing-package-gap-proof-spine}

The finite globalization interface is not a single primitive. It stands on three policies: asking, packaging, and gaps.

\begin{definition}[Package policy]
\(\PkgPol(\Pi,D)\) states that signatures generated from histories in \(D\) admit package tokens, that internally same signatures yield internally same packages, and that package sameness is grounded in internally same signatures.
\end{definition}

\begin{definition}[Gap policy]
\(\GapPol(\Pi,D)\) states that gap membership is determined by signatures and package tokens: a history is in the gap of a package precisely when it generates a signature belonging to that package.
\end{definition}

\begin{theorem}[Gap coverage]
Assume \(\AskPol(\Pi,D)\), \(\PkgPol(\Pi,D)\), and \(\GapPol(\Pi,D)\). If \(h\in D\), then there exists a package token \(p\) such that \(\InGap(\Pi,D,p,h)\).
\end{theorem}
\begin{proof}
By asking totality, generate a signature \(s\) of \(h\). By package existence, generate a package token \(p\) for \(s\). By the gap policy, \(h\) is a member of the gap of \(p\).
\end{proof}

\begin{theorem}[Gap separation]
Assume \(\AskPol(\Pi,D)\), \(\PkgPol(\Pi,D)\), and \(\GapPol(\Pi,D)\). If \(h\in D\), \(\InGap(\Pi,D,p,h)\), and \(\InGap(\Pi,D,q,h)\), then \(\PSame(p,q)\).
\end{theorem}
\begin{proof}
By the gap policy, gap membership yields signatures \(s,t\) of \(h\) packaged by \(p,q\). Signature determinacy gives \(\HSame(s,t)\). Package extensionality then yields \(\PSame(p,q)\).
\end{proof}

\begin{theorem}[Globalization classifies by signatures]
\label{thm:packages-classify-signatures}
Under \(\AskPol(\Pi,D)\), \(\PkgPol(\Pi,D)\), and \(\GapPol(\Pi,D)\), package tokens classify histories in \(D\) by signature sameness: histories with the same signature inhabit internally same packages, and histories in internally same grounded packages have internally same signatures.
\end{theorem}
\leanchecked{BEDC.FKernel.Package.packagePolicy\_classifies\_signatures}
\leanchecked{BEDC.FKernel.Package.PackagePolicy\_grounding\_witness}
\begin{proof}
The first direction follows from package extensionality. The second follows from package grounding. The gap policy connects package membership back to source histories, ensuring that the classification is not a detached visible label but a provenance-preserving package.
\end{proof}

\begin{definition}[Composite gap]
Given compression interfaces \(C:X\leadsto Y\) and \(D:Y\leadsto Z\), define a composite gap by
\[
\CompGap_{D\circ C}(z,x)
\]
when there exists an intermediate visible item \(y\) such that \(x\) lies in the \(C\)-gap of \(y\) and \(y\) lies in the \(D\)-gap of \(z\).
\end{definition}

\begin{theorem}[Composite gap coverage]
If the \(C\)-gap covers each source item and the \(D\)-gap covers each \(C\)-visible item, then the composite gap covers each source item.
\end{theorem}
\begin{proof}
Given a source item \(x\), choose a \(C\)-visible item \(y\) whose gap contains \(x\). Then choose a \(D\)-visible item \(z\) whose gap contains \(y\). By definition of composite gap, \(x\) lies in the composite gap of \(z\).
\end{proof}

\begin{corollary}[Ledger composition principle]
A composite compression has a ledger made of the first compression ledger plus the pullback of the second compression ledger along the first visible interface.
\end{corollary}
