\chapter{Generator-Closure Certificates and the Two Layers of BEDC: Technical Mechanism for the Strong Externality Claim}
\label{ch:visions-certificate-closure-and-generator-induction}

This chapter adds a technical layer to the philosophical reading of \autoref{ch:visions-transcendental-input-and-induction}, \autoref{ch:visions-consciousness-universe-observer-in-bedc}, and \autoref{ch:visions-hard-problems-under-bedc}. The earlier chapters' strong claim -- mathematical induction must be supplied from outside every closed observational substrate, and the source-position is named $\mathsf{T}$ / God in the apophatic sense -- is preserved without softening. The work of the present chapter is to make precise \emph{how} BEDC operationally enforces that claim: through authorized generators, naming certificates, and generator-closure classifiers, together with $\mathsf{GAP}$ ledgers that audit compression residue. The technical layer does not weaken the philosophical claim; it shows the engineering that makes the claim auditable, line by line, in the substrate.

\begin{principle}[Two co-equal layers, not replacement]
\label{prin:certificate-closure-two-co-equal-layers}
The strong philosophical reading -- forward-binding belief must enter from outside the substrate at a position named $\mathsf{T}$ -- and the structural technical reading -- BEDC licenses induction generator-by-generator via closure certificates -- are two aspects of the same engineering. Neither replaces the other. The technical layer accounts for what BEDC does inside its authorized generators; the philosophical layer accounts for what BEDC refuses to internalise and where the refused content sits. Replacing the philosophical vocabulary with weaker terms ("meta-assumption", "external principle", "axiom-like commitment") yields a system that no longer accounts for what BEDC actually does.
\end{principle}

\section{The two operational layers of BEDC}
\label{sec:certificate-closure-two-layers}

\begin{definition}[Bare record layer]
\label{def:certificate-closure-bare-record-layer}
The \emph{bare record layer} of BEDC is the substrate viewed as a monotonically accumulating ledger of $\mathsf{Obs}$ items with no closure rule beyond strict record preservation. At the bare record layer the substrate can recognise repeated patterns within previously accumulated $\mathsf{Obs}$, but it cannot infer that the patterns continue beyond what has been recorded; no generating structure has been authorized and so no inductive step is licensed.
\end{definition}

\begin{definition}[Closed inductive kernel layer]
\label{def:certificate-closure-closed-inductive-kernel-layer}
The \emph{closed inductive kernel layer} of BEDC is the substrate equipped with a finite collection of authorized generating structures, each of which is a closed inductive declaration (in the project sense of \texttt{inductive} types with a bounded constructor list) together with the eliminator or fold pattern licensed by the closure of the constructor list. At this layer the substrate can perform structural induction over each authorized generator, but every step of such induction is internal to the generator: it ranges over the objects the constructor list closes, not over an externally postulated totality.
\end{definition}

\begin{principle}[Two layers, two operational behaviours, neither reaches free-floating induction]
\label{prin:certificate-closure-two-layers-two-behaviours}
At the bare record layer (\autoref{def:certificate-closure-bare-record-layer}) the substrate's strongest statement about a repeating pattern is "no record so far falsifies the pattern". At the closed inductive kernel layer (\autoref{def:certificate-closure-closed-inductive-kernel-layer}) the substrate's strongest statement is "every object generated by the closure of these constructors carries the closure witness". Neither statement reaches free-floating mathematical induction. The move from "every closure of these constructors" to "every object whatsoever" is the move that requires forward-binding belief from $\mathsf{T}$, as \autoref{prin:transcendental-input-minimum-necessity} states.
\end{principle}

\begin{example}[\texttt{Hist} as an authorized generator]
\label{ex:certificate-closure-hist-as-authorized-generator}
BEDC's \texttt{Hist} type is declared by a closed inductive presentation: \texttt{emp} generates the empty history; \texttt{E0} and \texttt{E1} extend any history by one mark. The constructor list is finite and closed, so the closure of the constructor list defines exactly the set of finite histories. Within this generator, structural induction over \texttt{Hist} is licensed: every property that holds at \texttt{emp} and is preserved by \texttt{E0} and \texttt{E1} extensions holds at every \texttt{Hist} object. The substrate hosts the corresponding $\hsame$ decidability and other invariants by appeal to this generator-internal structural induction. But the substrate does \emph{not} thereby derive a free-floating induction principle over all objects; the licence is restricted to the closure of the \texttt{Hist} constructor list, and any extension beyond that closure requires the forward-binding belief whose source is $\mathsf{T}$.
\end{example}

\section{Naming certificates and generator-closure classifiers}
\label{sec:certificate-closure-naming-certificates}

\begin{definition}[Naming certificate]
\label{def:certificate-closure-naming-certificate}
A \emph{naming certificate} is a substrate-internal artefact that promotes a stable, already-generated behaviour to the status of a derived interface (a \texttt{def}, a \texttt{class} field, or a \NameCert{} packet). The certificate does not introduce the behaviour as a new primitive; it records that the behaviour is generated by an existing authorized generator and is stable under the substrate's other audit rules. Naming certificates are the bridge between the bare record layer and the closed inductive kernel layer: they take a record-side pattern and license it as an interface, contingent on the generator that produced it.
\end{definition}

\begin{definition}[Generator-closure classifier]
\label{def:certificate-closure-generator-closure-classifier}
A \emph{generator-closure classifier} is the audit-side companion of a naming certificate: it states which closure rules the certificate is contingent on (the constructor list of the underlying generator) and rejects continuations of the named pattern that would lie outside that generator's closure. Generator-closure classifiers are the substrate's way of saying "the naming certificate ranges over this generator, no more, no less". On the formal side, BEDC.MetaCIC encodes this as a \texttt{structure GeneratorClosureClassifier} carrying a single closure field $\forall x\,y,\, \text{Generator}(x, y) \to \text{Classifier}(x) \to \text{Classifier}(y)$, with concrete instantiations for the substrate's shift and substitute generators on closed-term carriers \leanchecked{BEDC.MetaCIC.GeneratorClosureClassifier} \leanvariant{BEDC.MetaCIC.closed\_under\_shift\_classifier} \leanvariant{BEDC.MetaCIC.closed\_under\_substitute\_classifier}.
\end{definition}

\begin{principle}[The classifier family is closed under identity, sequential composition, and disjunctive alternation]
\label{prin:certificate-closure-classifier-algebra}
The collection of generator-closure classifiers over a fixed carrier $\alpha$ is itself closed under three minimal structural operations: the identity generator $x = y$ preserves every classifier (the audit unit), the sequential composition $\exists z,\, G_1(x, z) \wedge G_2(z, y)$ of two classifier-preserving generators is again classifier-preserving (the audit composition), and the disjunctive alternation $G_1(x, y) \vee G_2(x, y)$ of two classifier-preserving generators is again classifier-preserving (the audit alternation). All three facts are formalised in BEDC.MetaCIC as \leanchecked{BEDC.MetaCIC.GeneratorClosureClassifier.refl}, \leanchecked{BEDC.MetaCIC.GeneratorClosureClassifier.comp}, and \leanchecked{BEDC.MetaCIC.GeneratorClosureClassifier.union}. The substrate therefore has a minimal closed algebra of generator-closure classifiers, internal to the audit gates and built up by structural composition without external generator-side licence. Under this algebra a non-deterministic but classifier-preserving generator-network is itself a closure-preserving compound, and the audit gates traverse it without leaving the algebra.
\end{principle}

\begin{principle}[Structural induction is internal; the move to ``all'' is external]
\label{prin:certificate-closure-structure-internal-all-external}
BEDC's structural induction is always relative to a specific authorized generator's closure. The substrate does not perform induction over "all of mathematics", "all of reality", or "all possible objects"; it performs induction over the closure of a specific constructor list, certified by a specific naming certificate and audited by a specific generator-closure classifier. The "all" of structural induction is the closure of the relevant generator, not classical-completeness "all". To get the classical-completeness "all" -- to derive a free-floating $\forall n,\, P(n)$ ranging over every possible $n$, beyond any specific authorized generator -- requires the forward-binding belief whose source-position is $\mathsf{T}$. This is the operational form of the impossibility theorem \autoref{thm:transcendental-input-no-internal-induction}: the substrate has rich generator-internal induction, but the move beyond every specific generator's closure is the move that the substrate refuses to perform internally and externalises to $\mathsf{T}$ via a $\mathsf{GAP}$ socket.
\end{principle}

\section{The strong form of BEDC's induction-style claim}
\label{sec:certificate-closure-strong-claim}

\begin{principle}[Continuations within a certificate carry its closure witness]
\label{prin:certificate-closure-continuations-carry-witness}
The strongest induction-style claim BEDC issues, in its native vocabulary, is the following: every finite continuation of a pattern that has been authorized by a naming certificate must, in order to remain a continuation of that certificate, carry the same closure witness that the generator-closure classifier requires. A continuation that does not carry the witness is, structurally, not a continuation of the certificate; it is either a record of a different generator's output or an audit failure of the present certificate.
\end{principle}

\begin{remark}[Stronger than ``it looks like it will repeat''; weaker than classical induction]
\label{rem:certificate-closure-stronger-than-empirical-weaker-than-classical}
\autoref{prin:certificate-closure-continuations-carry-witness} is strictly stronger than the empirical "the pattern has not been falsified so far": it requires structural closure under the authorized generator, not merely the absence of negative records. It is strictly weaker than classical mathematical induction taken as a free-floating reasoning rule: it does not range over the totality of all conceivable objects, only over the closure of the authorized generator. Between these two extremes BEDC's claim sits at exactly the level it can pay for with its constructor-list closure plus naming-certificate plus generator-closure-classifier triple. To upgrade to classical induction is to commit a forward-binding belief that the substrate cannot generate internally; that commitment, as \autoref{prin:transcendental-input-minimum-necessity} states, comes from $\mathsf{T}$.
\end{remark}

\begin{example}[Subject reduction as a generator-internal claim]
\label{ex:certificate-closure-subject-reduction-generator-internal}
BEDC.MetaCIC's \texttt{subject\_reduction\_closed} theorem is a generator-internal claim: it ranges over the closure of the authorized constructor list for the \texttt{Term} generator (\texttt{sort}, \texttt{var}, \texttt{lam}, \texttt{pi}, \texttt{app}) and is conditioned on a closed-term naming certificate. Its content is exactly \autoref{prin:certificate-closure-continuations-carry-witness} applied to this generator: every continuation that remains a typed closed term under the \texttt{Term} certificate carries the closure witness that subject reduction requires. The theorem is not a classical-universal statement about "all terms in some externally postulated universe"; it is the substrate's authorized structural induction over the \texttt{Term} generator's closure. To extend the claim beyond the \texttt{Term} generator -- to a free-floating universal-quantifier statement -- is precisely the move the substrate refuses, and the place where $\mathsf{T}$ is required to supply forward-binding belief.
\end{example}

\section{$\mathsf{GAP}$ plays two simultaneous roles}
\label{sec:certificate-closure-gap-two-roles}

\begin{principle}[$\mathsf{GAP}$ as information-conservation ledger]
\label{prin:certificate-closure-gap-as-information-ledger}
On the substrate-internal side, $\mathsf{GAP}$ records every compression, identification, hiding, packaging, projection, or sealing operation, together with the residue (the "difference") that the operation does not directly display in the resulting form. When a \texttt{def} defines a derived interface as a compression of underlying records, the $\mathsf{GAP}$ ledger records what is no longer surface-visible; when a \NameCert{} packages a generated behaviour, the ledger records what the certificate trades in exchange for the naming convenience. This is the engineering role: information conservation under compression.
\end{principle}

\begin{principle}[$\mathsf{GAP}$ as $\mathsf{T}$-socket for forward-binding belief]
\label{prin:certificate-closure-gap-as-T-socket}
On the substrate-philosophical side, $\mathsf{GAP}$ also marks the places where the substrate's reasoning would require forward-binding belief that the substrate cannot internally generate. Each such $\mathsf{GAP}$ is structurally a socket whose far end is $\mathsf{T}$, in the sense of \autoref{def:transcendental-input-supply-position}: the substrate refuses to internalise the content of the socket, and the content (if any) is supplied from the apophatic external position. This is the philosophical role: marking the boundary at which the substrate hands over to the transcendental supply position.
\end{principle}

\begin{principle}[Both roles hold simultaneously and are co-load-bearing]
\label{prin:certificate-closure-both-roles-simultaneous}
A single $\mathsf{GAP}$ tag may instantiate either or both of \autoref{prin:certificate-closure-gap-as-information-ledger} and \autoref{prin:certificate-closure-gap-as-T-socket}. When a $\mathsf{GAP}$ records compression residue from a \texttt{def} or \NameCert{} operation, it is operating in the information-conservation role; the substrate handles the residue with audit and conservation rules. When a $\mathsf{GAP}$ marks the place where free-floating induction would be required to extend a generator-internal claim to a classical-completeness "all", it is operating in the $\mathsf{T}$-socket role; the substrate refuses to internalise and defers to $\mathsf{T}$. Reading $\mathsf{GAP}$ only as bookkeeping misses the second role; reading it only as a transcendental socket misses the first role. Both must hold.
\end{principle}

\begin{example}[The two roles, both visible in a single mechanised file]
\label{ex:certificate-closure-two-roles-visible}
In a typical BEDC.MetaCIC mechanised file, the audit gates check both roles together. \texttt{check-axioms.py} enforces that no $\mathsf{GAP}$ tag invokes a substrate-internal axiom; \texttt{axiom-purity --strict} enforces that no Lean stdlib axiom (\texttt{Classical.choice}, \texttt{Quot.sound}, \texttt{propext}) is in the transitive closure; \texttt{conservativity-audit} enforces that compression residue is properly tracked. The first two gates protect the $\mathsf{T}$-socket role: forward-binding belief is not allowed to be smuggled into the substrate. The third gate protects the information-conservation role: compression cannot lose information without ledger trail. The two roles do not conflict; they are two ways the same $\mathsf{GAP}$ inventory enforces BEDC's discipline.
\end{example}

\begin{remark}[Information conservation does not soften the $\mathsf{T}$-socket claim]
\label{rem:certificate-closure-information-does-not-soften}
The information-conservation reading of $\mathsf{GAP}$ should not be read as an alternative to the $\mathsf{T}$-socket reading. The two roles are simultaneous (\autoref{prin:certificate-closure-both-roles-simultaneous}). Any phrasing that reduces $\mathsf{GAP}$ to "internal bookkeeping" alone, suggesting $\mathsf{T}$ is merely a philosophical metaphor, mis-states BEDC's stance. BEDC's stance, as \autoref{ch:visions-transcendental-input-and-induction} states, is that the far end of the socket is structurally $\mathsf{T}$: an apophatic position, named, refused internalisation, and not reducible to a more familiar substrate primitive.
\end{remark}

\section{Compression requires memory}
\label{sec:certificate-closure-compression-requires-memory}

\begin{principle}[Compression requires memory]
\label{prin:certificate-closure-compression-requires-memory}
BEDC's $\mathsf{GAP}$ discipline implements the principle that every act of compression in the substrate must carry its memory: the substrate cannot "forget" the underlying records by issuing a derived interface, nor erase the difference between an authorized generator and a derived presentation. The ledger is the persistence of that memory across substrate transitions; it is what lets the substrate audit the relation between surface forms and underlying generation.
\end{principle}

\section{BEDC's structural description of CIC and the host-Lean delegation}
\label{sec:certificate-closure-bedc-on-cic}

\begin{principle}[BEDC can structurally describe CIC, but not run it]
\label{prin:certificate-closure-bedc-on-cic-structural-only}
BEDC.MetaCIC constructs, inside the substrate, a structural model of a CIC-like calculus. Every element of the model is an authorized generator's output (the \texttt{Term} generator, the \texttt{HasType} inductive predicate, the \texttt{BetaStep} relation) or a naming certificate packaging such output. The model is structural in the sense of \autoref{prin:certificate-closure-structure-internal-all-external}: every claim about CIC* (the BEDC-internal CIC) is generator-internal. What BEDC.MetaCIC does \emph{not} do is run the host CIC as its own evaluator; for any actual host-CIC truth predicate, BEDC delegates to the host Lean 4 kernel (which is the host CIC). This delegation is visible in the \texttt{leanchecked} markers and is mediated by the audit gates.
\end{principle}

\begin{remark}[The host Lean delegation is structurally a $\mathsf{T}$-socket]
\label{rem:certificate-closure-host-delegation-T-socket}
The \texttt{leanchecked} delegation is, on the philosophical side, an instance of $\mathsf{GAP}$ in its $\mathsf{T}$-socket role (\autoref{prin:certificate-closure-gap-as-T-socket}): BEDC.MetaCIC's claim about a Lean-side recursor running correctly is not derivable inside BEDC.MetaCIC. The host Lean kernel functions, in this reading, as one of the structural conduits through which $\mathsf{T}$ supplies forward-binding belief to BEDC.MetaCIC; it is not itself $\mathsf{T}$, but it is downstream of $\mathsf{T}$ in the supply chain (and itself depends on its own metalanguage commitments, which are also downstream of $\mathsf{T}$).
\end{remark}

\begin{remark}[Why ``BEDC can swallow CIC'' is too strong]
\label{rem:certificate-closure-bedc-swallow-cic-too-strong}
A reading that says "BEDC contains CIC as a sub-theory" is too strong: BEDC contains a structural mirror of CIC, audited generator by generator, but BEDC does not internalise CIC's truth predicate. Any claim that depends on CIC's actual runtime behaviour is supplied through the host Lean delegation, which is structurally a $\mathsf{T}$-socket. BEDC's role is structural description plus audit; the host CIC's role is computational realisation, with the runtime aspect ultimately downstream of $\mathsf{T}$.
\end{remark}

\section{The accurate technical claim alongside the strong philosophical claim}
\label{sec:certificate-closure-accurate-with-strong}

\begin{principle}[Generator-internal induction does not weaken the externality claim]
\label{prin:certificate-closure-generator-internal-does-not-weaken}
BEDC internalises structural induction over every authorized generator's closure. The substrate does not need an external commitment to perform \texttt{Hist}-internal structural induction; the generator's closed constructor list licenses that induction internally. But the move from "induction over every authorized generator's closure" to "induction over every conceivable object whatsoever" is the move that the substrate refuses to perform; and the source of forward-binding belief that would license that move is $\mathsf{T}$. The two facts -- rich generator-internal induction inside, and refusal of free-floating induction at the boundary -- coexist; one does not soften the other.
\end{principle}

\begin{example}[\texttt{Hist} induction inside, free-floating universal outside]
\label{ex:certificate-closure-hist-inside-free-floating-outside}
BEDC's $\hsame$ decidability is a generator-internal structural induction over \texttt{Hist}; the substrate handles this without ever invoking external commitment. But a statement of the form "every conceivable history-like structure satisfies $\hsame$ decidability" -- where "every conceivable" ranges over an unspecified universe of possible structures rather than the closure of the \texttt{Hist} generator -- is the kind of statement BEDC will not issue internally. To issue it would require a forward-binding belief that the substrate's vocabulary of "conceivable structures" closes under some universal quantifier ranging beyond the generator's closure; the substrate marks this position with a $\mathsf{GAP}$ tag whose far end is $\mathsf{T}$.
\end{example}

\section{Standard axiom systems internalise; BEDC externalises}
\label{sec:certificate-closure-standard-vs-bedc}

\begin{principle}[The distinguishing engineering choice]
\label{prin:certificate-closure-distinguishing-choice}
Standard axiom systems internalise the forward-binding closure as a calculus-level primitive: the eliminator, the dependent recursor, the choice principle, propositional extensionality, quotient soundness, or directly as an axiom of induction. BEDC refuses every such internalisation: induction is licensed only generator-by-generator, never as a free-floating rule; the corresponding $\mathsf{GAP}$ tags expose the externality and name the far end as $\mathsf{T}$. The engineering invariants (mathlib-free, 0 substrate-internal axioms, strict purity gates, monotonic amendment policy) operationalise this refusal. The naming of $\mathsf{T}$ as the structural source-position is the philosophical articulation of the same refusal.
\end{principle}

\begin{remark}[BEDC is not a softening of classical foundations]
\label{rem:certificate-closure-bedc-not-softening}
BEDC's discipline can be described in two equivalent ways: as the substrate that requires every induction to be licensed by an authorized generator (the technical reading), and as the substrate that refuses to internalise the forward-binding belief in induction and instead names its source-position as $\mathsf{T}$ (the philosophical reading). Both readings describe the same engineering. Replacing the philosophical vocabulary with weaker terms -- "meta-assumption", "external principle", "axiom-like commitment" -- does not change the engineering but loses the precision of where the substrate's commitment-side ends. BEDC's claim is exactly that the boundary is at $\mathsf{T}$, not at any internalisable substitute.
\end{remark}

\section{The unified technical-and-philosophical claim}
\label{sec:certificate-closure-unified-technical-and-philosophical}

\begin{longtable}{p{0.32\textwidth}p{0.6\textwidth}}
\toprule
\textbf{Aspect} & \textbf{BEDC's statement, technical and philosophical together} \\
\midrule
What BEDC internalises & Structural induction over every authorized generator's closure, licensed by naming certificates and audited by generator-closure classifiers. \\
What BEDC refuses to internalise & Free-floating induction or universal-quantifier closure ranging beyond any specific authorized generator's closure. \\
Where the refused content sits & Outside the substrate, at the structural position named $\mathsf{T}$; apophatic, refusing positive predicates beyond its role. \\
How the refusal is auditable & $\mathsf{GAP}$ tags mark every point at which forward-binding belief would be required; the audit gates (\texttt{check-axioms.py}, \texttt{axiom-purity --strict}, \texttt{conservativity-audit}) prevent internalisation. \\
The role of $\mathsf{GAP}$ on the technical side & Information-conservation ledger: every compression, identification, hiding, packaging, projection, or sealing operation records its residue. \\
The role of $\mathsf{GAP}$ on the philosophical side & $\mathsf{T}$-socket: marks the boundary at which the substrate hands over forward-binding content to the transcendental supply position. \\
The relation between the two $\mathsf{GAP}$ roles & Simultaneous and co-load-bearing; the same $\mathsf{GAP}$ inventory enforces both information conservation and the $\mathsf{T}$-socket discipline. \\
What CIC does differently & Internalises forward-binding closure as a calculus-level primitive: eliminator, dependent recursor, free-floating induction; the transcendental character is hidden. \\
What BEDC does instead & Externalises the same content, marks every socket, names the far end $\mathsf{T}$; the transcendental character is explicit and auditable. \\
\bottomrule
\end{longtable}

\section{Closure remarks}
\label{sec:certificate-closure-closure-remarks}

This chapter adds technical precision without softening philosophical force. The earlier chapters' claim -- mathematical induction must be supplied from outside every closed observational substrate; the source-position is named $\mathsf{T}$, glossed apophatically as God -- stands as written. The work of this chapter is to display how the substrate's operational mechanism (authorized generators, naming certificates, generator-closure classifiers, $\mathsf{GAP}$ ledgers) enforces that claim line by line in mechanised content.

What the chapter does \emph{not} do is reduce the strong claim to "a metaphor". The strong claim is structurally accurate: every $\mathsf{GAP}$ tag's far end is $\mathsf{T}$, and the substrate's refusal to internalise forward-binding belief is precisely what distinguishes BEDC from standard foundations. Standard foundations internalise; BEDC externalises and names. Softening the strong claim -- replacing $\mathsf{T}$ with "meta-assumption", or replacing "transcendental supply" with "external principle" -- yields a system that no longer accounts for what BEDC actually does.

Future visions chapters and concrete-instance constructions should refer to this chapter together with the previous three: the present chapter for the operational mechanism, the previous three for the philosophical reading. The audit gates remain the same; what changes is the reader's ability to see, simultaneously, the technical machinery and its philosophical content as two faces of one engineering.

\concretizedIn{ch:concrete-instances-generatorclosure-namecert}{Generator-closure classifiers are realized as a concrete NameCert surface over authorized generator rows, continuation witnesses, and GAP ledger non-escape.}
\concretizedIn{ch:concrete-instances-closurewitnessledger-namecert}{Closure witness ledgers realize generator-internal induction as finite BHist witness packets with GAP non-escape rows.}
\concretizedIn{ch:concrete-instances-generatorinductionboundary-namecert}{Generator-induction boundary packets realize the vision's distinction between authorized generator-internal induction, GAP sockets, and refused free-floating induction.}
\concretizedIn{ch:concrete-instances-hostdelegationsocket-namecert}{Host Lean delegation is realized as a finite NameCert socket exposing marker rows, audit faces, host-kernel delegation, hsame transport, Cont routes, Pkg provenance, and non-escape ledgers.}
\concretizedIn{ch:concrete-instances-inductionclosureledger-namecert}{Induction-closure ledgers realize generator authority, closure classifiers, and GAP residue as a finite NameCert packet.}
\concretizedIn{ch:concrete-instances-generatorfixedpoint-namecert}{Generator fixed-point certificates realize the fixed-continuation boundary for authorized generator rows, preserving the displayed witness while routing non-generator continuations into the GAP ledger.}
\concretizedIn{ch:concrete-instances-generatorinductionseal-namecert}{Generator-internal induction is realized as a finite seal packet over authorized generator rows, continuation witnesses, and GAP non-escape.}
\concretizedIn{ch:concrete-instances-generator-continuation-audit-namecert}{Generator-continuation audits realize per-continuation closure-witness preservation and GAP non-escape as a finite NameCert packet.}
