\chapter{Closed-MetaCIC consistency assembly: a partial closure map}
\label{ch:closed-metacic-consistency-assembly}

\section{The setup}
\label{sec:closed-metacic-consistency-assembly-setup}

BEDC.MetaCIC aims at unconditional closed-term consistency of the substrate's
internal CIC fragment. The canonical path is the standard one: subject
reduction, strong normalisation on closed terms, and no closed normal proof of
$\mathsf{False}$. This chapter records which pieces of the path are already
discharged and which constitute the open frontier.

The relevant distinction is between closed-normal consistency and full closed
consistency. Closed-normal consistency speaks only about closed proof terms that
are already beta-strong. Full closed consistency would also need to transport an
arbitrary closed proof term along reduction until the normal-form theorem can be
applied. That transport is exactly the subject-reduction boundary.

\section{The assembled positive content}
\label{sec:closed-metacic-consistency-assembly-positive-content}

\subsection{Closed-term strong normalisation}
\label{subsec:closed-metacic-consistency-assembly-closed-sn}

The strong-normalisation content is available through the candidate-mediated
closed-term interface. The substrate verifies that an empty-context typed closed
term is strongly normalising when the appropriate candidate evidence is
supplied:
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_closedCandidate}
\leanvariant{BEDC.MetaCIC.closed\_typed\_term\_sn\_from\_candidateSet}.

These theorems are not themselves a closed subject-reduction theorem. They are
the normalisation side of the assembly path. They say that the candidate
interface can deliver termination of closed typed terms once the term has been
placed inside the relevant reducibility certificate.

\subsection{No closed-normal proof of False}
\label{subsec:closed-metacic-consistency-assembly-no-normal-false}

The contradiction-side theorem is also available:
\leanvariant{BEDC.MetaCIC.no\_closed\_normal\_proof\_of\_false}. The substrate
verifies that any closed proof term whose beta reduction is already strong
cannot inhabit the internal false encoding.

In formula form, the checked content has the shape:

$$
\begin{aligned}
  \mathsf{Closed}(t)
  \wedge
  \mathsf{BetaStrong}(t)
  \wedge
  \mathsf{HasType}([],t,\mathsf{False})
  &\Rightarrow
  \bot.
\end{aligned}
$$

The theorem is closed over normal-form inhabitants of $\mathsf{False}$. It does
not need to assert that every closed proof term can be reduced while preserving
its displayed type; that assertion belongs to the subject-reduction frontier.

\subsection{Closed-normal consistency assembly}
\label{subsec:closed-metacic-consistency-assembly-normal-assembly}

The substrate also has the direct assembly statement:
\leanvariant{BEDC.MetaCIC.closed\_normal\_consistency\_assembly}. It composes
empty-context typing, closedness, and beta-strong normality into a single
audit-checkable statement.

The theorem is the positive closed-normal node of the path:

$$
\begin{aligned}
  \mathsf{HasType}([],t,\mathsf{False})
  \wedge
  \mathsf{Closed}(t)
  \wedge
  \mathsf{BetaStrong}(t)
  &\Rightarrow
  \bot.
\end{aligned}
$$

Thus BEDC.MetaCIC already establishes the consistency statement for the
normal-form fragment. The remaining question is whether every closed proof of
$\mathsf{False}$ can be connected to that fragment without losing the typing
certificate.

\section{The unassembled frontier}
\label{sec:closed-metacic-consistency-assembly-frontier}

\subsection{Conditional subject reduction}
\label{subsec:closed-metacic-consistency-assembly-conditional-sr}

Subject reduction is available as a parameterised theorem in BEDC.MetaCIC,
conditional on four discharge hypotheses. Those hypotheses govern beta
substitution preservation, application-argument codomain stability,
lambda-domain preservation, and Pi-domain preservation. The interface is mapped
in \autoref{ch:metacic-subject-reduction-obstruction}.

This is the exact point where the closed-normal theorem would have to become a
full closed consistency theorem. A closed proof term of $\mathsf{False}$ must be
normalised, and the displayed false type must remain attached throughout the
reduction path. Without that preservation step, the normal-form theorem cannot
be applied to an arbitrary closed proof term.

\subsection{The closed reduction obstruction}
\label{subsec:closed-metacic-consistency-assembly-reduction-obstruction}

The substrate proves the closed reduction obstruction:
\leanvariant{BEDC.MetaCIC.closed\_consistency\_reduction\_obstruction\_not\_available}.
This theorem establishes that closed-term subject reduction is not directly
available on the present substrate. Consequently unconditional closed-term
consistency via the standard subject-reduction path is blocked at that node.

The obstruction does not weaken the positive closed-normal theorem. It locates
the missing lift. The available consistency theorem applies once beta-strong
normality is already part of the input; the unavailable theorem would justify
transporting arbitrary closed proofs to that input form.

\section{The assembly diagram}
\label{sec:closed-metacic-consistency-assembly-diagram}

The dependency map is:

\begin{verbatim}
Closed-term SN
  status: AVAILABLE
  witnesses:
    BEDC.MetaCIC.closed_typed_term_sn_from_candidate
    BEDC.MetaCIC.closed_typed_term_sn_from_closedCandidate
    BEDC.MetaCIC.closed_typed_term_sn_from_candidateSet

No closed-normal proof of False
  status: AVAILABLE
  witness:
    BEDC.MetaCIC.no_closed_normal_proof_of_false

Closed-normal consistency
  status: AVAILABLE
  witness:
    BEDC.MetaCIC.closed_normal_consistency_assembly

Closed reduction by subject reduction
  status: BLOCKED
  obstruction:
    BEDC.MetaCIC.closed_consistency_reduction_obstruction_not_available

Full closed consistency
  required inputs:
    Closed-normal consistency
    Closed reduction by subject reduction
  status: BLOCKED
  reason:
    the subject-reduction discharge is blocked
\end{verbatim}

The assembled node is therefore closed-normal consistency, not full closed
consistency. BEDC.MetaCIC establishes the normal-form sub-consistency
unconditionally. It cannot lift that statement to arbitrary closed proofs of
$\mathsf{False}$ without discharging the subject-reduction obligations.

\section{What this partial closure does establish}
\label{sec:closed-metacic-consistency-assembly-establishes}

The partial closure that already holds is strong. Any closed proof term that is
beta-strong cannot inhabit the internal $\mathsf{False}$ encoding. Equivalently,
the substrate rules out a closed false proof inside the normal-form fragment.

This is a non-trivial statement about normal-form inhabitants of
$\mathsf{False}$. The substrate has established not no-consistency-at-all but
consistency on the normal-form fragment. The positive theorem is narrow because
its input includes beta-strong normality, and it is sharp because its conclusion
is contradiction from a closed false proof under exactly that input.

\section{What discharge would buy}
\label{sec:closed-metacic-consistency-assembly-discharge-value}

Discharging all four subject-reduction obligations would buy the lift from
closed-normal consistency to unconditional closed consistency. The lift would
have the following shape:

$$
\begin{aligned}
  \mathsf{HasType}([],t,\mathsf{False})
  \wedge
  \mathsf{Closed}(t)
  &\Rightarrow
  \mathsf{HasType}([],n,\mathsf{False})
  \wedge
  \mathsf{Closed}(n)
  \wedge
  \mathsf{BetaStrong}(n)
\end{aligned}
$$

for a normal endpoint $n$ reached from $t$. The closed-normal consistency
assembly would then eliminate the right-hand side. The discharge would have to
traverse the dependent-codomain boundary identified in
\autoref{ch:metacic-subject-reduction-obstruction}.

\section{Apophatic framing}
\label{sec:closed-metacic-consistency-assembly-apophatic-framing}

The partial closure is itself an apophatic name. The substrate names what it has
and what it does not have, sharply. The unassembled frontier is not hidden
behind a proof hole; it is documented as four named hypotheses and an explicit
obstruction theorem.

This is the BEDC discipline applied to its own meta-theory: name the open cells,
and do not cover them with an informal appeal to the intended calculus. The
reader can see the positive assembled theorem, the blocked subject-reduction
node, and the exact reason full closed consistency is not claimed.

\concretizedIn{ch:concrete-instances-closed-normal-consistency-boundary-namecert}{Closed-normal MetaCIC consistency is realized as a finite boundary packet separating beta-strong consistency from the blocked subject-reduction lift.}

\section{Boundary}
\label{sec:closed-metacic-consistency-assembly-boundary}

This chapter records the present assembly state, not a proposal for discharging
the four obligations. The discharge problem is open and resides at the
dependent-codomain frontier identified in
\autoref{ch:metacic-subject-reduction-obstruction}.

\concretizedIn{ch:concrete-instances-normalfalseexclusion-namecert}{The normal-form false-proof exclusion is exposed as a concrete NameCert packet without claiming full closed consistency.}
\concretizedIn{ch:concrete-instances-closed-normal-consistency-namecert}{Closed-normal consistency is represented as a finite NameCert boundary separated from the subject-reduction obstruction.}
\concretizedIn{ch:concrete-instances-normal-form-consistency-seal-namecert}{The closed-normal consistency assembly is realized as a finite normal-form seal packet with an explicit subject-reduction boundary.}
