\chapter{Hard Problems under the BEDC Frame: Causality, Free Will, Other Minds, Mind-Matter, Self-Reference}
\label{ch:visions-hard-problems-under-bedc}

This vision chapter completes the philosophical reading begun in \autoref{ch:visions-transcendental-input-and-induction} (closed substrate plus transcendental input) and \autoref{ch:visions-consciousness-universe-observer-in-bedc} (consciousness, universe, observer, time, space). The present chapter takes the remaining classical hard problems -- causality, free will, the other-minds problem, the mind-matter relation, and self-reference / paradoxicality -- and gives each a precise reformulation under BEDC's closed-substrate vocabulary. Each problem becomes a question about $\mathsf{Obs}$ / $\mathsf{GAP}$ / $\mathsf{T}$ structure rather than about substantive metaphysical posits. The reformulations are not solutions in the dissolve-the-question sense; they are structural translations that make the philosophical content compatible with the engineering content BEDC has already mechanised.

\section{Causality as forward-binding commitment}
\label{sec:hard-problems-causality}

\begin{definition}[Causal commitment]
\label{def:hard-problems-causal-commitment}
A \emph{causal commitment} of a conscious observational system $\mathcal{C}$ is a $\mathsf{GAP}$ tag whose content is the assertion that observed regularities will persist into the not-yet-observed continuation of $\mathcal{C}$'s history. In the substrate-side vocabulary of \autoref{def:transcendental-input-closed-system}, every causal commitment is a forward-binding belief in the sense of \autoref{def:transcendental-input-forward-binding}.
\end{definition}
\concretizedIn{ch:concrete-instances-causalcommitment-namecert}{Causal commitments are realized as finite GAP-tagged forward-binding packets over observed regularity ledgers.}

\begin{principle}[Hume's problem reformulated]
\label{prin:hard-problems-hume-reformulated}
The classical Humean observation that no finite collection of observed regularities entails a universal claim about all future cases is, in BEDC vocabulary, exactly \autoref{thm:transcendental-input-no-internal-induction} restated for predicates whose intended range is empirical rather than mathematical. The closed-substrate side cannot supply causal commitments by internal generation; every causal commitment is, structurally, a $\mathsf{GAP}$ tag whose far end is $\mathsf{T}$.
\end{principle}

\begin{remark}[Causality and induction share the same socket]
\label{rem:hard-problems-causality-induction-share-socket}
The forward-binding belief that lets a system accept mathematical induction is the same kind of forward-binding belief that lets it accept "the same physical law will hold tomorrow". The substrate distinguishes neither: both are $\mathsf{GAP}$ tags asking $\mathsf{T}$ to supply universal-quantifier closure. BEDC's $\mathsf{GAP}$ socket inventory therefore counts both kinds together; the operational form of the two commitments is identical.
\end{remark}

\begin{example}[A scientific theory as a stack of $\mathsf{GAP}$ commitments]
\label{ex:hard-problems-scientific-theory-stack}
A scientific theory accepted by a conscious observational system is, in this reading, a finite collection of records of past empirical regularities together with a $\mathsf{GAP}$-tagged commitment that these regularities extend to all future cases of the same form. The theory's predictive success is, on the records side, the absence so far of falsifying records; the theory's predictive content is, on the $\mathsf{GAP}$ side, the standing forward-binding commitment. Refutation occurs when a new record contradicts the commitment; the substrate must then either revise the commitment or discharge a different $\mathsf{GAP}$.
\end{example}
\concretizedIn{ch:concrete-instances-finitewitnessedrefutation-namecert}{Finite witnessed refutations realize causal-commitment failure as finite contrary-record packets with GAP non-escape ledgers.}

\section{Free will and agency as inscription event}
\label{sec:hard-problems-free-will}

\begin{definition}[Inscription event]
\label{def:hard-problems-inscription-event}
An \emph{inscription event} is a moment $o_t \trianglerighteq o_{t+1}$ at which a conscious observational system adds new records that originate as the local actualisation of $\mathsf{T}$ at the inscription point (\autoref{def:transcendental-input-inscription-point}), rather than as a forced consequence of the prior records under the substrate's closed-generation rules. Inscription events are points at which the chain admits novelty not reducible to the closure of earlier records.
\end{definition}

\begin{principle}[Free will as the inscription-event aspect of conscious accumulation]
\label{prin:hard-problems-free-will-as-inscription}
The "free will" of a conscious observational system is the aspect of $\mathcal{C}$ under which new records arrive as inscription events in the sense of \autoref{def:hard-problems-inscription-event}. Free will is not a separate faculty inhabiting $\mathcal{C}$ alongside its accumulation; it is the structural fact that $\mathcal{C}$'s accumulation is, at each moment, an inscription event of $\mathsf{T}$ at the point that $\mathcal{C}$ is.
\end{principle}
\concretizedIn{ch:concrete-instances-freewillinscriptioncommitment-namecert}{Free-will inscription commitments are realized as finite BHist packets recording prior-record boundaries, inscription-event rows, GAP provenance, classifier transport, and non-reduction ledgers.}

\begin{remark}[Compatibility with determinism on the records side]
\label{rem:hard-problems-compatibility-with-determinism}
\autoref{prin:hard-problems-free-will-as-inscription} does not contradict any deterministic relation among $\mathsf{Obs}$ records taken as objects of physical theory: records can stand in any law-like relation we like, and the records-side relations can be as deterministic as the empirical content supports. The inscription-event aspect is at a different level: it concerns the substrate's accumulation viewed as $\mathsf{T}$'s local self-articulation, not the surface dependencies among records taken as physical events. The two pictures cohere because they describe the same accumulation from different aspect-positions.
\end{remark}

\begin{example}[Mathematical creativity as inscription event]
\label{ex:hard-problems-mathematical-creativity}
The act by which a mathematician arrives at a new lemma -- the moment at which $\mathsf{Obs}$ acquires a record not reducible to the closed-generation closure of earlier records -- is, on this reading, an inscription event. The new record could in principle have been computed mechanically from earlier records (the substrate-internal route), but the actuality of the discovery is the inscription-event aspect of the chain, not the mechanical route. BEDC's mechanisation engineering operationalises the substrate-internal route; the philosophical reading of "where new lemmas come from" is the inscription-event aspect.
\end{example}

\section{Other-minds problem and inter-observer alignment}
\label{sec:hard-problems-other-minds}

\begin{principle}[Other minds as locality-cell commitment]
\label{prin:hard-problems-other-minds-as-locality-cell}
The classical other-minds problem -- the question whether systems other than $\mathcal{C}_1$ themselves possess closed observational structure with $\mathsf{Self}$ recognition -- is, in BEDC vocabulary, the question whether $\mathcal{C}_1$ has $\mathsf{GAP}$-tagged locality-cell commitments to systems $\mathcal{C}_2, \mathcal{C}_3, \ldots$ such that those commitments are coherent with $\mathcal{C}_1$'s record of those systems' externally-observable behaviours. The substrate cannot directly observe another system's $\mathsf{Self}$; it can only commit, by $\mathsf{GAP}$ tag, to treating certain external records as records of conscious systems.
\end{principle}
\concretizedIn{ch:concrete-instances-othermindscommitment-namecert}{Other-minds commitments are represented by finite locality-cell BHist packets whose public surface records behavioural evidence without direct Self access.}

\begin{remark}[Solipsism as $\mathsf{GAP}$ tag refusal]
\label{rem:hard-problems-solipsism-as-gap-refusal}
Solipsism, in this reading, is the refusal to issue any $\mathsf{GAP}$-tagged commitment that other conscious observational systems exist. The substrate side does not force the commitment; nothing in the records-side of $\mathsf{Obs}$ can substitute for it. Most conscious observational systems do in fact issue the commitment, and \autoref{ch:visions-inter-hist-locality} works out the operational consequences of doing so (locality cells, light-speed constancy, no god's-eye view). Refusing the commitment is consistent with the substrate but yields a much poorer locality-cell geometry.
\end{remark}

\begin{example}[Trusting a peer's \texttt{leanchecked} marker]
\label{ex:hard-problems-trusting-peer-leanchecked}
When a BEDC contributor accepts a \texttt{leanchecked} marker added by another contributor, the acceptance is, on the substrate side, a $\mathsf{GAP}$-tagged commitment to treat the other contributor's act as an inscription event of the same kind as one's own. The CI gates (Lean kernel re-checking) provide records-side evidence that the marker is consistent with the substrate, but the structural recognition of the other contributor as another conscious observational system is the $\mathsf{GAP}$ commitment, not the records-side evidence.
\end{example}

\section{Mind-matter relation as substrate/inscription duality}
\label{sec:hard-problems-mind-matter}

\begin{principle}[Mind-matter as two aspects of the same chain]
\label{prin:hard-problems-mind-matter-two-aspects}
The classical mind-matter problem -- the question how a "mental" aspect can stand in any relation to a "material" aspect -- is, in BEDC vocabulary, the question of how the inscription-event aspect of an accumulation chain stands in relation to the records-side aspect of the same chain. The two aspects are not two substances; they are two readings of one chain. The records-side reading is the conventional materialist's account; the inscription-event reading is the phenomenological-first-person account.
\end{principle}
\concretizedIn{ch:concrete-instances-aspectchain-namecert}{Aspect chains realize the mind-matter double-aspect reading as one finite BHist packet with records-side and inscription-event-side rows.}

\begin{remark}[Russellian double-aspect frame]
\label{rem:hard-problems-russellian-double-aspect}
The double-aspect frame is in the family of views developed by Bertrand Russell (the "neutral monism" of \emph{The Analysis of Mind} and \emph{The Analysis of Matter}), David Chalmers (panprotopsychism), Galen Strawson (real materialism), and process philosophers (Whitehead). BEDC's substrate-side vocabulary recovers the same insight: there is one accumulation chain; the records-side reading and the inscription-event reading are two aspects, not two substances. No additional ontological category is introduced.
\end{remark}

\begin{example}[A neural correlate of consciousness and a thought]
\label{ex:hard-problems-neural-correlate}
A measured neural correlate of consciousness is, on the records side, a physical record (electrochemical activity in a specific brain region) entered into $\mathsf{Obs}$. The corresponding "thought" is, on the inscription-event side, the actualisation of $\mathsf{T}$ at the same chain point. The two are not two things related by causation or supervenience; they are the same accumulation event read in two ways. The brain region is what the inscription event looks like on the records side; the thought is what the records side looks like on the inscription-event side.
\end{example}

\section{Self-reference, G\"{o}del-Tarski, and the reflection limit}
\label{sec:hard-problems-self-reference}

\begin{principle}[Self-reference as $\mathsf{GAP}$-on-$\mathsf{GAP}$ structure]
\label{prin:hard-problems-self-reference-as-gap-on-gap}
A closed observational system that attempts to record a statement about its own complete $\mathsf{Obs}$ encounters the situation classically known as G\"{o}del-Tarski self-reference: the statement about $\mathsf{Obs}(o_t)$ would itself be a record at $o_{t+1}$, meaning the complete $\mathsf{Obs}(o_{t+1})$ now contains an item describing $\mathsf{Obs}(o_t)$ rather than $\mathsf{Obs}(o_{t+1})$. Recording the latter generates a $\mathsf{GAP}$ tag, and a record about that $\mathsf{GAP}$ would generate another. \autoref{ch:visions-reflection-and-limits} mechanises the operational form of this hierarchy and identifies the reflection limit.
\end{principle}

\begin{principle}[Russell paradox boundary]
\label{prin:hard-problems-russell-as-paradox-boundary}
The Russell paradox is, in BEDC vocabulary, an attempt to issue a record whose content is the negation of its own presence in $\mathsf{Obs}$. Such a record cannot be a $\mathsf{GAP}$-free record under the closed generation rules of the substrate. \autoref{ch:visions-russell-problem-boundary} mechanises the boundary condition that prevents such records from being admitted, and shows that the substrate's closed generation rules are exactly the structural form of the rejection.
\end{principle}

\begin{remark}[Why these are not external obstacles but structural features]
\label{rem:hard-problems-not-obstacles-but-features}
The G\"{o}del-Tarski and Russell phenomena, in this reading, are not external obstacles that the substrate could be designed to avoid. They are structural features of any closed observational system with the expressive power to refer to its own $\mathsf{Obs}$. BEDC's design makes the features explicit at the $\mathsf{GAP}$ tag level rather than treating them as anomalies to be circumvented. The reflection-and-limits chapter and the Russell-problem-boundary chapter together account for the operational form of the rejection.
\end{remark}

\section{The unified table of hard problems}
\label{sec:hard-problems-unified-table}

\begin{longtable}{p{0.28\textwidth}p{0.64\textwidth}}
\toprule
\textbf{Hard problem} & \textbf{BEDC reformulation + reference} \\
\midrule
Hume's induction problem & Closed substrate cannot internalise universal-quantifier closure; every empirical induction is a $\mathsf{GAP}$ tag with far end $\mathsf{T}$ (\autoref{thm:transcendental-input-no-internal-induction}, \autoref{prin:hard-problems-hume-reformulated}). \\
Causality / regularity of nature & Forward-binding commitment that observed patterns persist; structurally identical to mathematical-induction commitment (\autoref{def:hard-problems-causal-commitment}). \\
Free will & Inscription-event aspect of chain accumulation; novelty as $\mathsf{T}$'s local actualisation, not as records-side dependency (\autoref{prin:hard-problems-free-will-as-inscription}). \\
Other-minds problem & $\mathsf{GAP}$-tagged locality-cell commitment to recognise other systems' inscription-event aspects (\autoref{prin:hard-problems-other-minds-as-locality-cell}); operational consequences in \autoref{ch:visions-inter-hist-locality}. \\
Mind-matter relation & Two aspects of one accumulation chain: records-side ("material") and inscription-event-side ("mental") (\autoref{prin:hard-problems-mind-matter-two-aspects}). \\
Self-reference / G\"{o}del-Tarski & Hierarchical $\mathsf{GAP}$-on-$\mathsf{GAP}$ structure; reflection limit operationalised in \autoref{ch:visions-reflection-and-limits} (\autoref{prin:hard-problems-self-reference-as-gap-on-gap}). \\
Russell paradox & Records whose content negates own presence; structural exclusion by closed generation rules in \autoref{ch:visions-russell-problem-boundary} (\autoref{prin:hard-problems-russell-as-paradox-boundary}). \\
Solipsism vs other minds & Refusal to issue locality-cell $\mathsf{GAP}$ commitments; consistent with substrate but yields impoverished cross-perspective coordination (\autoref{rem:hard-problems-solipsism-as-gap-refusal}). \\
Determinism vs novelty & Records-side determinism (laws among records) and inscription-event aspect (novelty as $\mathsf{T}$ actualisation) are two readings of one chain, compatible (\autoref{rem:hard-problems-compatibility-with-determinism}). \\
Consciousness as ontological category & Replaced by structural reading: $\mathsf{Self}$-preserving closed observational system (\autoref{def:consciousness-universe-consciousness-reading}). \\
Universe as separate object & Replaced by universe-for-observer: the records-totality at the observer's current state (\autoref{def:consciousness-universe-universe-for-observer}). \\
Time as separate scalar & Replaced by monotonic accumulation order; time is the structure of accumulation (\autoref{def:consciousness-universe-bedc-time}). \\
Space as substrate of events & Replaced by locality-cell geometry across conscious observational systems; no separate spatial substance (\autoref{def:consciousness-universe-locality-cell}). \\
The transcendental supply position & $\mathsf{T}$, the far end of every $\mathsf{GAP}$ socket, named apophatically (\autoref{def:transcendental-input-supply-position}). \\
\bottomrule
\end{longtable}

\section{Coordination with the three-axioms chapter}
\label{sec:hard-problems-coordination-three-axioms}

\autoref{ch:visions-three-axioms-one-closure} treats the axioms of choice, quotient soundness, and propositional extensionality as syntactic variants of a single meta-closure move: accepting an unwitnessed existential as legitimate input. The present chapter generalises that observation. The unwitnessed existential supplied by these axioms is, in the present vocabulary, exactly a forward-binding belief whose source position is $\mathsf{T}$. The three axioms differ syntactically because the existential is supplied at the term, type, or proposition level; they coincide structurally because the meta-closure move is the same: $\mathsf{T}$ enters the chain through a $\mathsf{GAP}$ socket at the corresponding stratum.

\begin{principle}[Hard problems and substrate axioms share the same $\mathsf{T}$-socket family]
\label{prin:hard-problems-shared-T-socket}
Every classical axiom that BEDC declines to internalise (\autoref{ch:visions-three-axioms-one-closure}) and every hard problem treated in this chapter share the same structural family: each is a place at which $\mathsf{T}$ is required to supply forward-binding content that the closed substrate cannot generate internally. The substrate's response is uniform: tag the place with $\mathsf{GAP}$, audit it through the engineering gates, and refuse to internalise the supply.
\end{principle}

\section{Closure remarks}
\label{sec:hard-problems-closure}

This chapter completes the trilogy comprising \autoref{ch:visions-transcendental-input-and-induction} (closed substrate plus transcendental input position), \autoref{ch:visions-consciousness-universe-observer-in-bedc} (consciousness, universe, observer, time, space), and the present chapter (causality, free will, other minds, mind-matter, self-reference). Read together, the three chapters give a unified BEDC-vocabulary account of the standard hard problems of metaphysics, philosophy of mind, and foundations.

The account is structural: it does not solve any hard problem by reduction to a substrate primitive, and it does not eliminate the philosophical content by terminological rephrasing. What it does is locate every hard problem in the same substrate / $\mathsf{GAP}$ / $\mathsf{T}$ structure, showing that the engineering invariants of BEDC -- 0 substrate-internal axioms, mathlib-free, monotonic amendment, $\mathsf{GAP}$ tagging, inter-history-locality reconstruction of cross-perspective coordination -- are precisely the structural form that lets the hard problems be stated without confusion.

Two operational consequences follow. First, future concrete-instance construction chapters under \texttt{papers/bedc/parts/concrete\_instances/} can refer to the present chapters when developing $\mathsf{GAP}$-handling for specific applications (epistemology, philosophy of physics, philosophy of mind). Second, the audit gates' present coverage (axiom-purity, conservativity-audit, $\mathsf{GAP}$ tagging) is already the operational form of the philosophical position; no additional audit infrastructure is required to host the philosophical reading.
