\chapter{MetaCIC Substitution module audit map}
\label{ch:metacic-substitution-audit-map}

\section{The setup}
\label{sec:metacic-substitution-audit-map-setup}

The BEDC.MetaCIC substitution submodule is the syntax layer that supports
movement across binders. It is split across five sibling files:
\texttt{Basic}, \texttt{ClosedComposition}, \texttt{Core},
\texttt{NatShift}, and \texttt{Statements}. The split exposes a useful audit
shape. Arithmetic facts about de Bruijn indices are kept separate from raw
substitution facts, closedness facts, and higher substitution statements.

The operations are \texttt{shift} and \texttt{substitute}. The first raises
free indices at or above a cutoff. The second replaces the variable at a
depth and adjusts indices around the removed binder. Both are ordinary
recursive operations on the closed \texttt{Term} generator. The audit question
is therefore not whether the operations exist, but which classifier boundary
they preserve and under which hypotheses.

The current closure state is exact. Closedness at a boundary makes both
operations inert at that boundary. Closed source and closed payload hypotheses
also support a small family of closed composition laws. The module also names
larger target shapes for shift--substitute and substitute--substitute
interaction, while the closed composition file provides the checked fragment
that is available without a general unclosed commutation theorem.

\section{Core operations}
\label{sec:metacic-substitution-audit-map-core-operations}

\subsection{\texttt{shift\_closed}}
\label{subsec:metacic-substitution-audit-map-shift-closed}

The boundary theorem for shift is
\leanvariant{BEDC.MetaCIC.shift\_closed}. It says that if a term is closed at
cutoff $n$, then shifting at $n$ by one leaves the term unchanged:

$$
\begin{aligned}
  \mathsf{ClosedAt}(n,t)
  &\Rightarrow
  \mathsf{shift}(n,1,t)=t.
\end{aligned}
$$

This is a classifier-preservation fact in its strongest local form. The term
has no free index reaching the cutoff, so the shift branch has no occurrence
to act on. The binder cases are not hidden semantic assumptions; they are the
recursive cases of the \texttt{ClosedAt} witness, where the boundary advances
under lambda and Pi.

The theorem is intentionally narrow. It does not state that arbitrary shifting
preserves every typing or reduction property. It states only that a term
already closed below the cutoff is syntactically fixed by the shift attempted
at that cutoff.

\subsection{\texttt{substitute\_closed}}
\label{subsec:metacic-substitution-audit-map-substitute-closed}

The matching boundary theorem for substitution is
\leanvariant{BEDC.MetaCIC.substitute\_closed}. It says that if a term is
closed at depth $d$, then substituting any payload at $d$ leaves the term
unchanged:

$$
\begin{aligned}
  \mathsf{ClosedAt}(d,t)
  &\Rightarrow
  \mathsf{substitute}(d,v,t)=t.
\end{aligned}
$$

The payload $v$ is arbitrary because the replacement site is absent. For every
variable index visible in $t$, the closedness witness supplies the inequality
placing that index below $d$. Hence the equality branch does not fire, and the
decrement branch does not fire. The recursive cases carry the same argument
through application, lambda, Pi, and sort.

This is the main closed-substitution closure law used by the paper side. It
is not a beta-substitution typing theorem. It is a syntactic boundary theorem:
substitution at a boundary cannot alter a term whose free-variable budget is
already below that boundary.

\subsection{Closed composition}
\label{subsec:metacic-substitution-audit-map-closed-composition}

The closed composition file supplies the checked fragment of substitution
composition that is available under closed payload and closed source
hypotheses. The central theorem is
\leanvariant{BEDC.MetaCIC.substitute\_compose\_closed\_both}. It specialises
the depth-indexed theorem
\leanvariant{BEDC.MetaCIC.substitute\_compose\_closed\_both\_at\_depth} to
depth $0$:

$$
\begin{aligned}
  &\mathsf{ClosedAt}(0,v)
  \wedge
  \mathsf{ClosedAt}(0,u)
  \wedge
  \mathsf{ClosedAt}(1,t) \\
  &\Rightarrow
  \mathsf{substitute}(0,v,\mathsf{substitute}(0,u,t))
  =
  \mathsf{substitute}(0,\mathsf{substitute}(0,v,u),t).
\end{aligned}
$$

The same file also records a closed swap law
\leanvariant{BEDC.MetaCIC.substitute\_swap\_closed} and a shift-after-
substitution bridge
\leanvariant{BEDC.MetaCIC.substitute\_after\_shift\_one\_closed}. These are
closed-fragment algebra, not unrestricted substitution calculus.

The audit distinction matters. \texttt{Statements.lean} names broad target
shapes, including \leandef{BEDC.MetaCIC.ShiftSubstituteStatement} and
\leandef{BEDC.MetaCIC.SubstituteSubstituteStatement}. The checked composition
theorems above are the current closed slice of that algebra. The manuscript
may cite the closed slice, but it must not cite an unrestricted
substitute--substitute commutation theorem unless such a theorem exists under
the same Lean namespace.

\section{Connection to subject reduction}
\label{sec:metacic-substitution-audit-map-subject-reduction}

Substitution is one of the necessary ingredients for MetaCIC subject
reduction. The subject-reduction obstruction map in
\autoref{ch:metacic-subject-reduction-obstruction} isolates the beta-redex
obligation as $\mathrm{BetaSubstitutionPreservation}$: typing must survive
when an argument is substituted into a binder body and the codomain is read
back through the same substitution.

The substitution module audited here is lower-level. It proves syntactic
closedness and closed composition facts about \texttt{Term}. Those facts are
necessary for a disciplined beta case, but they are not the whole beta typing
obligation. The typing obligation also mentions context lookup, body typing,
argument typing, codomain substitution, and the dependent type assigned after
the beta step.

Thus the connection is a handoff, not an identification. The substitution
module supplies the syntax-side closure laws that any subject-reduction
discharge must respect. The subject-reduction boundary remains the four-input
interface described in \autoref{ch:metacic-subject-reduction-obstruction}.
Closing syntactic substitution does not by itself close dependent typing
preservation.

\section{Connection to GeneratorClosureClassifier}
\label{sec:metacic-substitution-audit-map-generator-closure}

The same closure state has a certificate-theoretic reading. In
\autoref{def:certificate-closure-generator-closure-classifier}, a
generator-closure classifier records that a generator action preserves a
classifier. The concrete MetaCIC instances are
\leanvariant{BEDC.MetaCIC.closed\_under\_shift\_classifier} and
\leanvariant{BEDC.MetaCIC.closed\_under\_substitute\_classifier}.

These two instances read the \texttt{shift} and \texttt{substitute} operations
as authorized generators over the closed-term carrier. Their classifier is
\texttt{ClosedAt} at the relevant boundary. The closure field says that when
the operation is applied inside the admitted slice, the result stays inside
that slice.

The algebra of \autoref{prin:certificate-closure-classifier-algebra} then
explains why these local facts compose with the wider BEDC audit machinery.
Identity, sequential composition, alternation, sub-generator restriction, and
finite iteration preserve classifier closure once the corresponding local
classifier witnesses are present. The substitution module provides concrete
local witnesses for two important MetaCIC generators; the algebra explains how
such witnesses can be routed through larger certificate networks without
changing their scope.

\section{Apophatic framing}
\label{sec:metacic-substitution-audit-map-apophatic}

This chapter names a positive closure layer without turning it into a larger
claim. BEDC can say exactly what the substitution module supplies: boundary
inertness for shift and substitution, closed-source composition fragments,
and classifier instances for the two generator actions. It also says what the
module does not supply: unrestricted substitution commutation, closed subject
reduction, or a hidden semantic equality principle for terms.

The apophatic point is methodological. The manuscript must not fill a missing
dependent-typing bridge by appealing to the existence of syntactic
substitution lemmas. The available lemmas are real, checked, and useful, but
their scope is the closed syntactic layer.

\section{Boundary}
\label{sec:metacic-substitution-audit-map-boundary}

This chapter records the present closure state of
\texttt{BEDC.MetaCIC.Substitution}. It may be used to cite the checked
boundary theorems \texttt{shift\_closed} and \texttt{substitute\_closed}, the
closed composition theorems in \texttt{ClosedComposition.lean}, the named
statement shapes in \texttt{Statements.lean}, and the concrete
GeneratorClosureClassifier instances for shift and substitution.

It does not claim an unrestricted substitution calculus. It does not claim
that $\mathrm{BetaSubstitutionPreservation}$ is discharged. It does not claim
the full closed subject-reduction theorem excluded by
\autoref{ch:metacic-subject-reduction-obstruction}. The substitution closure
state is a necessary building block for those routes, not their endpoint.

\concretizedIn{ch:concrete-instances-metacic-substitution-audit-packet-namecert}{Substitution audit rows are realized as a finite NameCert packet for closed syntax movement and subject-reduction handoff boundaries.}
