\chapter{MetaCIC Decidable module audit map}
\label{ch:metacic-decidable-audit-map}

\section{The setup}
\label{sec:metacic-decidable-audit-map-setup}

The BEDC.MetaCIC decidable submodule records the executable checking surface
around the closed syntax and typing fragment. It is split across
\texttt{CheckClosedAtom}, \texttt{CheckClosed},
\texttt{CheckCompleteness}, \texttt{GalleryTests}, and
\texttt{NormalEqDecide}. The split separates structural equality, type
inference, completeness wrappers, gallery-level coverage, and bounded
normal-form comparison.

The audit question is not whether the substrate imports a global classical
decision principle. It does not. The checked content is a family of concrete
procedures over the closed \texttt{Term} generator, together with soundness,
completeness, and gallery sanity theorems for the procedures that are present.

\section{What is established}
\label{sec:metacic-decidable-audit-map-established}

The checked inventory has five parts.

\begin{itemize}
\item Structural term equality is Boolean and correct:
  \leanvariant{BEDC.MetaCIC.Term.eq}
  \leanvariant{BEDC.MetaCIC.Term.eq\_correct}
  \leanvariant{BEDC.MetaCIC.checkSameTerm\_sound}
  \leanvariant{BEDC.MetaCIC.checkSameTerm\_complete}.
\item Type inference for the displayed checking fragment is sound and complete
  with respect to the corresponding \texttt{HasType} rules:
  \leanvariant{BEDC.MetaCIC.inferTypeCtx\_sound}
  \leanvariant{BEDC.MetaCIC.inferTypeCtx\_complete}
  \leanvariant{BEDC.MetaCIC.inferTypeCtxClosed\_sound}
  \leanvariant{BEDC.MetaCIC.inferTypeCtxClosed\_complete}.
\item The completeness file exposes constructor-shaped witnesses for sort,
  variable, Pi, lambda, and application cases:
  \leanvariant{BEDC.MetaCIC.inferTypeCtx\_complete\_strict}
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_app}
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_lam}
  \leanvariant{BEDC.MetaCIC.CheckCompleteness.inferTypeCtx\_complete\_pi}.
\item The bounded normal-form comparison layer is executable and sound once
  finished normalisation witnesses are supplied:
  \leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_refl}
  \leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_true\_eq\_normalized}
  \leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_sound\_finished}
  \leanvariant{BEDC.MetaCIC.decideClosedBetaConv\_sound\_finished\_betaConv}.
\item The gallery tests give finite closed witnesses for the Church boolean,
  natural, pair, option, list, sum, and polymorphic examples:
  \leanvariant{BEDC.MetaCIC.gallery\_sanity\_all\_typed\_witnesses}.
\end{itemize}

This is a real executable layer. The paper may cite structural equality
checking, the inferencer's soundness and completeness for the represented
typing rules, bounded normal-form comparison under finished-normalisation
witnesses, and gallery sanity over the displayed examples.

\section{Boundary}
\label{sec:metacic-decidable-audit-map-boundary}

The decidable module does not export a global decision procedure for every
MetaCIC meta-theoretic property. It does not decide subject reduction, strong
normalisation, arbitrary confluence, or full closed consistency. Its strongest
public shape is local: executable equality and typing checks for the displayed
syntax, plus bounded conversion comparison when the normalisation witnesses
needed by the soundness theorem are already present.

Thus this audit map supplies the decidable-checking side of the MetaCIC
overview. It is orthogonal to the subject-reduction obstruction in
\autoref{ch:metacic-subject-reduction-obstruction}, the confluence
substitution boundary in \autoref{ch:metacic-confluence-audit-map}, and the
candidate-mediated normalisation interface in
\autoref{ch:metacic-normalization-audit-map}.

