\section{The observation--reflection equivalence thesis}
\label{sec:observation-and-reflection}

The preceding sections establish the route to the equivalence thesis. Physical fit is finite and open. Mathematical approximation does not imply physical adequacy. Ontic state is the stable source of reality-facing signatures. Physical modelling proceeds through ledgered approximation towers. Physical induction is a stability certificate over open continuation. Objectivity is invariant stability across observer histories rather than a privileged view.

The central claim is structural:
$$
\text{physical inquiry and MetaCIC self-study share the same reflective architecture}.
$$
This does not identify physical reality with a formal system, nor MetaCIC with a physical object. It says that both operate through finite histories, signature extraction, classifier-mediated packaging, certificate-based stabilization, ledgered compression, and open continuation.

The BEDC kernel already displays this pattern:
$$
b_0,b_1
\to
\Hist
\to
\mathsf{msame},\mathsf{hsame}
\to
\mathsf{Ext},\mathsf{Cont}
\to
\mathsf{Ask}
\to
\mathsf{Sig}
\to
\mathsf{sameSig}
\to
\mathsf{Pkg}
\to
\mathsf{Gap}
\to
\mathsf{NameCert}.
$$
Derived interfaces are not primitive exports. They are licensed by certificates whose fields record source, pattern, classifier, stability, and ledger. Physical modelling has the same epistemic form: a model is licensed by source traces, extracted patterns, physical classifiers, stability certificates, and ledgers recording what the model hides.

\begin{definition}[Reflective inquiry architecture]
\label{def:reflective-inquiry-system}
A reflective inquiry architecture is a tuple
$$
\mathcal R
=
(S,H,\Sigma,\mathcal C,\mathcal P,\mathcal L,\mathcal E),
$$
where $S$ is a source domain, $H$ is a finite-history carrier generated from the source, $\Sigma$ extracts signatures, $\mathcal C$ classifies signatures into visible sameness classes, $\mathcal P$ is a package, model, or derived interface licensed by the classifier, $\mathcal L$ is a ledger recording hidden source material, and $\mathcal E$ is an open continuation procedure. Its generic chain is
$$
S
\to
H
\to
\Sigma(H)
\to
\mathcal C(\Sigma)
\to
\mathcal P
\to
\mathcal L
\to
\mathcal E.
$$
The architecture is reflective when it can use finite histories and certificates to generate higher-level descriptions of its own behaviour while still lacking an internal final truth oracle.
\end{definition}

\begin{definition}[Physical inquiry instance]
\label{def:physical-inquiry-instance}
A physical inquiry instance of reflective architecture is obtained by setting $S$ to a reality-facing source, $H$ to finite observation traces, $\Sigma$ to observed physical signatures, $\mathcal C$ to the model--data classifier, $\mathcal P$ to a physical model or law certificate, $\mathcal L$ to the experimental and approximation ledger, and $\mathcal E$ to the future observation horizon. Its chain is
$$
R
\to
H_n(R)
\to
\operatorname{ObsSig}_{\Pi}(R\mid H_n)
\to
\operatorname{Fit}_n(M,R;\Pi)
\to
\operatorname{LawCert}(M,R;\Pi)
\to
\operatorname{Ledger}
\to
\operatorname{OpenFit}.
$$
\end{definition}

\begin{definition}[MetaCIC self-study]
\label{def:metacic-self-study}
A MetaCIC self-study instance of reflective architecture is obtained by setting $S$ to formal generative behaviour, $H$ to generated $\Hist$ values, $\Sigma$ to signatures extracted by Ask/Sig interfaces, $\mathcal C$ to licensed classifiers such as $\mathsf{hsame}$, $\mathsf{sameSig}$, or derived classifiers, $\mathcal P$ to packages or derived interfaces, $\mathcal L$ to gap and NameCert ledgers, and $\mathcal E$ to open meta-level continuation. Its chain is
$$
\Hist
\to
\mathsf{Cont}
\to
\mathsf{Ask}/\mathsf{Sig}
\to
\text{classifier}
\to
\mathsf{Pkg}/\mathsf{NameCert}
\to
\text{ledger}
\to
\operatorname{OpenMeta}.
$$
\end{definition}

\begin{definition}[Observation--reflection equivalence]
\label{def:observation-reflection-equivalence}
Physical inquiry and MetaCIC self-study are observation--reflection equivalent when there is a structure-preserving correspondence
$$
\Phi:
\mathcal R_{\mathrm{phys}}
\longrightarrow
\mathcal R_{\mathrm{MetaCIC}}
$$
whose component roles match as follows:
$$
\begin{array}{c|c}
\text{physical inquiry} & \text{MetaCIC self-study}\\
\hline
\text{physical system} & \text{formal source or kernel behaviour}\\
\text{finite observation trace} & \Hist\\
\text{measurement continuation} & \mathsf{Cont}\\
\text{observed signature} & \mathsf{Sig}\\
\text{model classifier} & \text{licensed classifier}\\
\text{model package} & \mathsf{Pkg}\text{ or derived interface}\\
\text{experimental ledger} & \mathsf{Gap}\text{ or NameCert ledger}\\
\text{prediction horizon} & \text{open meta continuation}\\
\text{no final-fit oracle} & \text{no internal truth predicate}
\end{array}
$$
The equivalence is architectural, not ontological.
\end{definition}

\begin{definition}[Reflection gap]
\label{def:reflection-gap}
A reflection gap is the gap between a system's finite certified self-description and a total truth predicate for that system. In physical inquiry it appears as the difference between
$$
\operatorname{Fit}_n(M,R;\Pi)
$$
and
$$
\forall H,\;
\operatorname{Fit}(M,R;\Pi\mid H).
$$
In MetaCIC it appears as the difference between structural self-description and an internal truth predicate for the system.
\end{definition}

\begin{definition}[Internalization without finalization]
\label{def:internalization-without-finalization}
A system has internalization without finalization when it can internalize finite descriptions, certificates, and structural reproductions of its own behaviour, but cannot internally certify that these descriptions are final, total, or truth-complete.
\end{definition}

\begin{definition}[Reflective stability certificate]
\label{def:reflective-stability-certificate}
A reflective stability certificate shows that a self-description can be reused under specified continuations without collapsing into a total truth oracle. In physical inquiry this is a law or induction certificate. In MetaCIC it is a NameCert, stability certificate, or derived-interface certificate whose reuse remains below the open meta-loop boundary.
\end{definition}

\section{Physical and formal reflective instances}
\label{sec:physical-formal-reflective-instances}

\begin{theorem}[Physical inquiry instantiates reflective architecture]
\label{thm:physical-inquiry-instantiates-reflective-architecture}
Physical inquiry has the form of a reflective inquiry architecture.
\end{theorem}

\begin{proof}
Let the source be a physical system $R$. The observer does not access $R$ as a completed totality; access is mediated by finite traces $H_n(R)$. These traces are organized by an observation bundle $\Pi$ into signatures $\operatorname{ObsSig}_{\Pi}(R\mid H_n)$. A model $M$ generates corresponding model signatures, and a classifier compares the two:
$$
\operatorname{ModSig}_{\Pi}(M\mid H_n)
\sim_{\Pi}
\operatorname{ObsSig}_{\Pi}(R\mid H_n).
$$
Successful comparison produces a finite fit certificate. Reuse of the model requires stability data, and the source traces, approximations, hidden residues, and failure surfaces must be ledgered. Future observations remain open continuations. These are exactly the fields of \autoref{def:reflective-inquiry-system}.
\end{proof}

\begin{corollary}[Physical modelling is self-descriptive]
\label{cor:physical-modelling-self-descriptive}
A physical model describes not only a source object but also the observational process by which that object became modelable.
\end{corollary}

\begin{proof}
By \autoref{thm:physical-inquiry-instantiates-reflective-architecture}, the model is licensed by traces, signatures, classifiers, stability certificates, and ledgers. These components are part of the model's epistemic status, so the model records its own access route.
\end{proof}

\begin{corollary}[Physical theory is reflective without being subjective]
\label{cor:physical-theory-reflective-not-subjective}
Physical theory is reflective because it records conditions of observational access, but it is not subjective because reality-generated signatures may defeat model-generated signatures.
\end{corollary}

\begin{proof}
Reflectivity follows from the certificate structure of \autoref{thm:physical-inquiry-instantiates-reflective-architecture}. Non-subjectivity follows because finite fit fails whenever observed signatures separate from model signatures under the active classifier.
\end{proof}

\begin{theorem}[MetaCIC self-study instantiates reflective architecture]
\label{thm:metacic-self-study-instantiates-reflective-architecture}
MetaCIC self-study has the form
$$
\Hist
\to
\mathsf{Cont}
\to
\mathsf{Sig}
\to
\text{classifier}
\to
\mathsf{Pkg}/\mathsf{NameCert}
\to
\text{ledger}
\to
\operatorname{OpenMeta}.
$$
\end{theorem}

\begin{proof}
In BEDC, generated histories are extended by continuation. Ask and Sig interfaces expose visible data. Classifiers such as $\mathsf{hsame}$, $\mathsf{sameSig}$, package-sameness, or derived classifiers organize that visible data. Packages and derived interfaces are admitted only through certificate discipline. The NameCert template requires source, pattern, classifier, stability, and ledger fields. The meta-level remains open: the ground loop closes so the system can start, while the meta loop does not close into an internal truth predicate. Thus MetaCIC self-study instantiates \autoref{def:reflective-inquiry-system}.
\end{proof}

\begin{corollary}[MetaCIC self-study is structural, not totalizing]
\label{cor:metacic-self-study-structural-not-totalizing}
MetaCIC can structurally describe its own generative behaviour without producing a total internal truth predicate.
\end{corollary}

\begin{proof}
By \autoref{thm:metacic-self-study-instantiates-reflective-architecture}, self-study proceeds through histories, classifiers, packages, certificates, and ledgers while preserving the open meta-loop boundary.
\end{proof}

\section{The equivalence thesis}
\label{sec:observation-reflection-equivalence-thesis}

\begin{theorem}[Observation--reflection equivalence]
\label{thm:physical-inquiry-metacic-reflective-architecture}
Physical inquiry and MetaCIC self-study are observation--reflection equivalent.
\end{theorem}

\begin{proof}
By \autoref{thm:physical-inquiry-instantiates-reflective-architecture}, physical inquiry instantiates reflective inquiry architecture. By \autoref{thm:metacic-self-study-instantiates-reflective-architecture}, MetaCIC self-study instantiates the same architecture. The correspondence sends reality-facing source to formal generative source, finite observation trace to $\Hist$, measurement continuation to $\mathsf{Cont}$, observed signature to $\mathsf{Sig}$, model classifier to licensed classifier, model or law certificate to $\mathsf{Pkg}/\mathsf{NameCert}$, experimental ledger to gap or NameCert ledger, and open prediction horizon to open meta-continuation.

Each side proceeds from finite trace to visible signature, from signature to classifier, from classifier to package, from package to ledgered certificate, and from certificate to open continuation. Neither side possesses a final oracle: physical inquiry lacks a final-fit oracle over all possible observations, and MetaCIC lacks an internal truth predicate for itself. The structural roles and open-boundary conditions are preserved.
\end{proof}

\begin{corollary}[Physical inquiry is MetaCIC-like in form]
\label{cor:physical-inquiry-metacic-like-form}
Physical inquiry is not identical to MetaCIC, but it has the same epistemic skeleton.
\end{corollary}

\begin{proof}
\autoref{thm:physical-inquiry-metacic-reflective-architecture} establishes structural equivalence, not source identity. The two sides may differ in material source and empirical content while sharing finite histories, signatures, classifiers, certificates, ledgers, and open continuation.
\end{proof}

\begin{corollary}[MetaCIC self-study is physics-like in openness]
\label{cor:metacic-self-study-physics-like-openness}
MetaCIC self-study resembles physical inquiry in that its self-description remains open at the meta-boundary.
\end{corollary}

\begin{proof}
Physical inquiry remains open because later observations may defeat present models. MetaCIC remains open because total self-truth cannot be internalized. By \autoref{thm:physical-inquiry-metacic-reflective-architecture}, both open boundaries occupy the same architectural role.
\end{proof}

\section{Architectural equivalence}
\label{sec:architectural-equivalence}

\begin{definition}[Architectural equivalence]
\label{def:architectural-equivalence}
Two inquiry systems are architecturally equivalent when their roles, transitions, certificates, ledgers, and open boundaries correspond, even if their source domains differ. Architectural equivalence preserves inquiry form, not object substance.
\end{definition}

\begin{definition}[Ontological identity]
\label{def:ontological-identity}
Two systems are ontologically identical only when their source domains, objects, operations, and truth conditions coincide. The present framework does not assert ontological identity between physical reality and MetaCIC.
\end{definition}

\begin{theorem}[Observation--reflection equivalence is architectural]
\label{thm:observation-reflection-architectural-not-ontological}
Observation--reflection equivalence does not imply that physical reality is a formal system or that MetaCIC is a physical system.
\end{theorem}

\begin{proof}
The equivalence preserves the roles of finite trace, signature, classifier, package, ledger, and open continuation. It does not identify the source domains. In physical inquiry, the source is a reality-facing system capable of producing observations that may defeat the model. In MetaCIC self-study, the source is formal generative behaviour inside a certificate-governed framework. These sources are not the same object.
\end{proof}

\begin{corollary}[Structural equivalence does not erase empirical content]
\label{cor:structural-equivalence-empirical-content}
Even when physical inquiry and MetaCIC self-study share the same form, physical inquiry still requires empirical signatures.
\end{corollary}

\begin{proof}
The physical side contains reality-generated traces. Those traces are not supplied by MetaCIC syntax; they are obtained through interaction with physical systems.
\end{proof}

\begin{corollary}[Formal reflection does not replace experiment]
\label{cor:formal-reflection-not-experiment}
MetaCIC can clarify the architecture of inquiry, but it cannot supply the physical signatures needed to certify a model of reality.
\end{corollary}

\begin{proof}
Physical adequacy requires agreement between model-generated and reality-generated signatures. Formal reflection can describe the required certificate structure, but it cannot generate empirical observations.
\end{proof}

\section{Internalization, reflection gaps, and failure surfaces}
\label{sec:internalization-reflection-gaps-failure-surfaces}

\begin{theorem}[Internalization does not imply finalization]
\label{thm:internalization-does-not-imply-finalization}
If a system internalizes a description of its own behaviour, it does not follow that the system has finalized its own truth.
\end{theorem}

\begin{proof}
Internalization constructs a representation, certificate, or model of some aspect of behaviour. Finalization would require a total truth predicate or final-fit oracle for all continuations. A finite or certificate-mediated self-description can succeed locally without covering all future extensions, refinements, or meta-level truth conditions.
\end{proof}

\begin{corollary}[Observation protocols do not make theories final]
\label{cor:observation-protocols-not-final}
A physical theory can include its own measurement model, calibration rules, and uncertainty structure while remaining open to later failure.
\end{corollary}

\begin{proof}
Such inclusion internalizes observational access. By \autoref{thm:internalization-does-not-imply-finalization}, internalization does not imply finality.
\end{proof}

\begin{corollary}[Syntax internalization does not define truth]
\label{cor:syntax-internalization-not-truth}
A formal system may represent its own syntax or proof structure without defining a total truth predicate for itself.
\end{corollary}

\begin{proof}
This is the formal instance of \autoref{thm:internalization-does-not-imply-finalization}. Structural self-description does not supply a truth predicate for the whole system.
\end{proof}

\begin{definition}[Reflection failure surface]
\label{def:reflection-failure-surface}
A reflection failure surface is the class of continuations, refinements, or meta-queries that may expose the difference between certified local description and total truth. In physical inquiry it includes later observations, refined bundles, and hidden residues. In MetaCIC it includes attempted internal truth predicates, total halting predicates, or closure of the open meta loop.
\end{definition}

\begin{theorem}[Reflection gaps remain internally open]
\label{thm:reflection-gaps-internally-open}
Neither the physical reflection gap nor the formal reflection gap can be closed from within the corresponding finite inquiry process.
\end{theorem}

\begin{proof}
Closing the physical gap would require a final-fit oracle certifying fit over all admissible actual and counterfactual histories. Finite observation supplies only finite traces and stability certificates over specified continuation classes. Closing the formal gap would require an internal truth predicate for the system's own language or proof structure, which is exactly the meta-loop closure blocked by Tarski-style obstruction. Both gaps therefore remain internally open.
\end{proof}

\begin{corollary}[Failure surfaces are necessary]
\label{cor:failure-surfaces-necessary}
A theory without a failure surface is not more complete; it is less well-certified.
\end{corollary}

\begin{proof}
A failure surface records where finite certification may fail. By \autoref{thm:reflection-gaps-internally-open}, total closure is internally unavailable. Removing the failure surface hides the reflection gap rather than closing it.
\end{proof}

\begin{corollary}[Empirical revisability is open reflection]
\label{cor:empirical-revisability-open-reflection}
Empirical revisability in physics corresponds to open meta-reflection in MetaCIC.
\end{corollary}

\begin{proof}
In physics, revisability means that later observation may defeat current fit. In MetaCIC, open reflection means that structural self-description does not become total truth. Both express the same continuation boundary.
\end{proof}

\section{NameCert as bridge concept}
\label{sec:namecert-bridge-concept}

\begin{definition}[Physical NameCert analogue]
\label{def:physical-namecert-analogue}
A physical NameCert analogue for a model $M$ of a system $R$ is
$$
\operatorname{PhysNameCert}(M,R;\Pi)
=
(\operatorname{SourceSpec},
\operatorname{PatternSpec},
\operatorname{ClassifierSpec},
\operatorname{StabilityCert},
\operatorname{LedgerPolicy}).
$$
It is the physical version of the BEDC certificate template.
\end{definition}

\begin{theorem}[Physical models require NameCert-like structure]
\label{thm:physical-models-require-namecert-like-structure}
Every physically serious model must supply source, pattern, classifier, stability, and ledger fields.
\end{theorem}

\begin{proof}
A model needs a source specification to state which observations licensed it, a pattern specification to state what regularity it claims, a classifier to state how model and reality are compared, a stability certificate to support prediction beyond finite fit, and a ledger policy because approximation hides information that may later become active. These are precisely the fields of \autoref{def:physical-namecert-analogue}.
\end{proof}

\begin{corollary}[A law is a certified name]
\label{cor:law-certified-name}
A physical law is a certified name for a stable pattern in reality-facing signatures.
\end{corollary}

\begin{proof}
By \autoref{thm:physical-models-require-namecert-like-structure}, a law must carry source, pattern, classifier, stability, and ledger data. The equation is only the visible pattern field.
\end{proof}

\begin{corollary}[The model name is certificate-bounded]
\label{cor:model-name-certificate-bounded}
A model's epistemic strength depends on the strength of its source, classifier, stability, and ledger fields.
\end{corollary}

\begin{proof}
Without source the model is ungrounded. Without classifier it cannot be compared to observation. Without stability it cannot predict. Without ledger it cannot recover hidden residues. The name is licensed only to the extent that its certificate fields are supplied.
\end{proof}

\section{Reflective towers and open self-description}
\label{sec:reflective-towers-open-self-description}

\begin{definition}[Reflective tower]
\label{def:reflective-tower}
A reflective tower is an approximation tower in which each level is a certified description of the preceding level:
$$
L_i
\to
\operatorname{Desc}(L_i)
=
L_{i+1}.
$$
The tower is reflective because each stage turns prior behaviour into a new visible object.
\end{definition}

\begin{definition}[Safe reflection]
\label{def:safe-reflection}
A reflective tower is safe when each level carries a ledger of hidden source material, each operation used at a higher level descends through the classifier of the lower level, and no level claims to be the total truth of the entire tower.
\end{definition}

\begin{theorem}[Certified approximation towers are reflective]
\label{thm:certified-approximation-towers-reflective}
If each compression arrow in an approximation tower extracts a pattern from the previous level and packages it as a visible object, then the tower is reflective.
\end{theorem}

\begin{proof}
A reflective tower requires each level to be a certified description of the preceding level. A compression arrow extracts source material, applies a classifier, records a pattern, packages a visible endpoint, and stores hidden material in a ledger. This is exactly the formation of a description of the previous level.
\end{proof}

\begin{corollary}[Idealization is reflection under compression]
\label{cor:idealization-reflection-under-compression}
An ideal object at the top of a tower is a reflected and compressed description of lower-level source behaviour.
\end{corollary}

\begin{proof}
Ideal objects are produced by repeated extraction, stabilization, smoothing, completion, or packaging. By \autoref{thm:certified-approximation-towers-reflective}, each stage is reflective when it records a certified description of the previous stage.
\end{proof}

\begin{corollary}[Tower collapse is unsafe reflection]
\label{cor:tower-collapse-unsafe-reflection}
Tower collapse occurs when a higher-level self-description is treated as identical to the lower-level source without a descent certificate.
\end{corollary}

\begin{proof}
Safe reflection requires ledgered compression and descent. Tower collapse removes these conditions and treats the endpoint as the source.
\end{proof}

\begin{definition}[Open self-description]
\label{def:open-self-description}
An inquiry process is an open self-description when it constructs descriptions of its own access conditions while leaving continuation and failure surfaces open.
\end{definition}

\begin{theorem}[Scientific inquiry is open self-description]
\label{thm:scientific-inquiry-open-self-description}
Physical scientific inquiry is an open self-description of reality-facing access.
\end{theorem}

\begin{proof}
Scientific inquiry records observations, constructs models, specifies classifiers, defines measurement protocols, estimates uncertainty, records failure conditions, and revises models when observations change. It describes not only reality but also the conditions under which reality becomes available to inquiry. It nevertheless does not close all future observations into a final object.
\end{proof}

\begin{corollary}[Scientific realism is certificate realism]
\label{cor:scientific-realism-certificate-realism}
A realist account of scientific models should attach realism to certified signature preservation, not to bare model--reality identity.
\end{corollary}

\begin{proof}
By \autoref{thm:scientific-inquiry-open-self-description}, scientific inquiry is open self-description. By \autoref{thm:physical-models-require-namecert-like-structure}, physical models require certificate structure. Realism therefore attaches to certified reality-facing signature preservation under specified conditions.
\end{proof}

\begin{corollary}[The world constrains self-description]
\label{cor:world-constrains-self-description}
Open self-description is not free construction, because reality-generated signatures can defeat model-generated signatures.
\end{corollary}

\begin{proof}
A model must match observed signatures under the active classifier. If reality generates a separating signature, finite fit fails.
\end{proof}

\section{Equivalence diagram}
\label{sec:equivalence-diagram}

The equivalence thesis can be summarized as:
$$
\begin{array}{ccccccccc}
\text{physics:}
&
R
&\to&
H_n
&\to&
\operatorname{ObsSig}_{\Pi}
&\to&
\operatorname{FitCert}
\to
\operatorname{LawCert}
\to
\operatorname{OpenFit}
\\
\Phi
&&&&&&&&
\\
\text{MetaCIC:}
&
\Hist
&\to&
\mathsf{Cont}
&\to&
\mathsf{Sig}
&\to&
\text{classifier}
\to
\mathsf{NameCert}
\to
\operatorname{OpenMeta}.
\end{array}
$$
The vertical correspondence preserves finite source access, signature extraction, classifier-mediated packaging, ledgered compression, certificate-governed reuse, and open continuation. It does not preserve source identity: $R$ is not $\Hist$, a laboratory is not a kernel, and a physical event is not a formal constructor.

\begin{theorem}[Equivalence diagram commutes at certification level]
\label{thm:equivalence-diagram-commutes-certification}
The observation--reflection diagram commutes when each physical modelling step is mapped to its corresponding MetaCIC certificate role.
\end{theorem}

\begin{proof}
A physical observation trace maps to a Hist-level trace. Signature extraction maps to Ask/Sig generation. Model--data classification maps to licensed classifier comparison. Model packaging maps to package or derived-interface formation. Experimental ledgering maps to gap or NameCert ledgering. Prediction maps to open continuation under stability. Following the physical path and then applying $\Phi$ therefore yields the same certificate roles as first applying $\Phi$ to the source-access structure and then following the MetaCIC path.
\end{proof}

\begin{corollary}[Equivalence is certificate-preserving]
\label{cor:equivalence-certificate-preserving}
Observation--reflection equivalence preserves source, pattern, classifier, stability, and ledger roles.
\end{corollary}

\begin{proof}
\autoref{thm:equivalence-diagram-commutes-certification} states that the diagram commutes at the level of certification. The relevant certificate fields are source, pattern, classifier, stability, and ledger.
\end{proof}

\begin{remark}[Compressed form]
\label{rem:observation-reflection-compressed-form}
The thesis is:
$$
\text{truth-like scientific content}
=
\text{finite signature fit}
+
\text{stability certificate}
+
\text{ledgered provenance}
+
\text{open continuation}.
$$
Physical inquiry is not a view from outside reality; it is a finite reflective process inside reality. MetaCIC is not a total self-truth machine; it is a finite reflective process inside a formal generative system. Both construct stable, certificate-governed signatures while refusing final meta-closure.
\end{remark}

\concretizedIn{ch:concrete-instances-observationreflectionpacket-namecert}{ObservationReflectionPacketUp realizes the observation--reflection equivalence as a finite source, history, signature, classifier, package, ledger, and open-continuation NameCert packet.}
\concretizedIn{ch:concrete-instances-reflective-stability-namecert}{ReflectiveStabilityUp realizes reflective stability as a finite source, checkpoint, classifier, open-continuation, transport, ledger, and NameCert packet.}
\concretizedIn{ch:concrete-instances-reflection-gap-boundary-namecert}{ReflectionGapBoundaryUp realizes the gap between finite certified self-description and total truth as a finite inquiry, ledger, continuation, and boundary NameCert packet.}
\concretizedIn{ch:concrete-instances-reflective-inquiry-namecert}{The reflective inquiry architecture is realized as a finite NameCert packet relating physical inquiry and MetaCIC self-study through source, signature, classifier, package, ledger, and open-continuation rows.}
\concretizedIn{ch:concrete-instances-finite-observation-reflection-seal-namecert}{Finite observation-reflection seals realize the physical inquiry and MetaCIC self-study correspondence as a finite NameCert packet with shared classifier, ledger, and non-finalization rows.}
