\section{Objectivity without a privileged observer}
\label{sec:objectivity-without-privileged-observer}

Physical induction leaves inquiry locally closed and globally open. This changes the meaning of objectivity. If no observer stands outside the inquiry process, and if no final-fit oracle is internally available, objectivity cannot be access to reality from nowhere. It must be reconstructed as invariant stability across admissible observer histories, observation bundles, and continuation procedures.

This is the physical reading of the multi-Hist layer. A multi-Hist configuration contains several local histories without a required common base, clock, or time-step indexing. Since an observer is identified with the history of recorded distinctions, there is no observer-substance behind the record and no privileged frame above the configuration. Frame-independent physical content must therefore live in inter-history invariants.

\begin{definition}[Observer history]
\label{def:reality-observer-history}
An observer history is a finite or extendable history $h\in\Hist$ interpreted as the record of distinctions, observations, continuations, and classifier-mediated signatures available to an observer. The observer is not an additional substance behind $h$; it is the history considered as a finite distinction record.
\end{definition}

\begin{definition}[Multi-observer configuration]
\label{def:reality-multi-observer-configuration}
A multi-observer configuration is a finite family
$$
\mathcal H=(h_1,\ldots,h_m)
$$
of observer histories considered together without assuming a shared origin, shared clock, shared time-step indexing, or privileged synchronizing observer.
\end{definition}

\begin{definition}[Privileged observer]
\label{def:reality-privileged-observer}
A privileged observer for $\mathcal H$ is a hypothetical observer history $h_\star$ that synchronizes, orders, and evaluates every $h_i\in\mathcal H$ from a distinguished standpoint. Equivalently, it would supply a global observational frame
$$
h_\star:(h_1,\ldots,h_m)
\longmapsto
\text{one shared empirical ordering}.
$$
The framework does not assume such a history.
\end{definition}

\begin{definition}[Inter-observer relation and invariant]
\label{def:reality-inter-observer-relation-invariant}
An inter-observer relation is a relation $R(h_i,h_j)$ whose evidence is obtained through finite observation, continuation, classifier, or ledger data available within the relevant histories. An inter-observer invariant is a function or predicate $I(h_i,h_j)$ whose value is stable under change of observational anchor:
$$
I(h_i,h_j)\sim I(h_j,h_i)
$$
up to the relevant history and signature classifiers. It may depend on relations between histories, but it may not privilege one history as the absolute frame.
\end{definition}

\begin{definition}[Relational objectivity]
\label{def:relational-objectivity}
A claim $\varphi$ is relationally objective over $\mathcal H$ when there is an inter-observer invariant $I$ such that $\varphi$ is determined by $I$ rather than by one observer history alone:
$$
\operatorname{Obj}_{\mathcal H}(\varphi)
\quad\Longleftrightarrow\quad
\exists I\;
\bigl(
I\;\text{is inter-observer invariant}
\;\wedge\;
I\Rightarrow\varphi
\bigr).
$$
Objectivity is therefore not observer-free; it is observer-invariant.
\end{definition}

\begin{definition}[Private and frame-independent content]
\label{def:private-frame-independent-content}
A claim $\varphi$ is private observational content of $h_i$ when it is determined only by the internal trace of $h_i$ and no inter-observer invariant transports it across the configuration. A claim is frame-independent physical content when it is relationally objective over every admissible multi-observer configuration in which it is asserted.
\end{definition}

\section{No global observer}
\label{sec:no-global-observer}

\begin{theorem}[No member is privileged by membership]
\label{thm:no-member-privileged-by-membership}
No element of a multi-observer configuration is privileged merely by being a member of the configuration.
\end{theorem}

\begin{proof}
By \autoref{def:reality-multi-observer-configuration}, the configuration supplies only a finite family of local histories. Membership does not give a shared origin, clock, time-step indexing, or synchronization map. Thus $h_i\in\mathcal H$ gives the local observational trace of $h_i$, but not authority to order or evaluate all other histories from a global frame.
\end{proof}

\begin{corollary}[Single histories are not frame-independent carriers]
\label{cor:single-history-not-frame-independent-carrier}
An individual observer history may carry valid local content, but it does not by itself carry frame-independent physical content.
\end{corollary}

\begin{proof}
By \autoref{thm:no-member-privileged-by-membership}, no observer history is privileged by default. A claim contained only in one history is therefore local to that history until transported by an inter-observer invariant.
\end{proof}

\begin{theorem}[Adding observers does not create an external view]
\label{thm:adding-observers-no-external-view}
Extending $\mathcal H=(h_1,\ldots,h_m)$ to $(h_1,\ldots,h_m,h_{m+1})$ does not by itself produce a privileged observer.
\end{theorem}

\begin{proof}
The added history is itself an observer history with its own finite trace and local continuation structure. It does not automatically contain the classifiers, ledgers, or time-step orderings of the other histories. If a candidate observer-of-observers is represented internally, it becomes another history and remains subject to the same locality constraints.
\end{proof}

\begin{corollary}[No internal observer-of-observers]
\label{cor:no-internal-observer-of-observers}
There is no observer-of-observers inside the same observational layer.
\end{corollary}

\begin{proof}
An internal candidate is added as another history. By \autoref{thm:adding-observers-no-external-view}, such addition does not create global synchronization.
\end{proof}

\section{Objectivity as invariance}
\label{sec:objectivity-as-invariance}

\begin{definition}[Anchor change]
\label{def:anchor-change}
An anchor change is the redescription of an inter-observer relation from the standpoint of another observer history:
$$
(h_i\;\text{as anchor})
\leadsto
(h_j\;\text{as anchor}).
$$
A quantity is stable under anchor change when its value remains classifier-equivalent after redescription.
\end{definition}

\begin{definition}[Anchor-stable claim]
\label{def:anchor-stable-claim}
A claim $\varphi$ is anchor-stable over $\mathcal H$ when, for all $h_i,h_j\in\mathcal H$,
$$
\varphi^{h_i}\sim\varphi^{h_j},
$$
where $\varphi^{h_i}$ denotes the expression of $\varphi$ with $h_i$ as observational anchor.
\end{definition}

\begin{definition}[Invariant certificate]
\label{def:invariant-certificate}
An invariant certificate for $\varphi$ over $\mathcal H$ is
$$
\operatorname{InvCert}(\varphi;\mathcal H)
=
(\operatorname{HistSources},
\operatorname{RelationSpec},
\operatorname{ClassifierSpec},
\operatorname{AnchorStability},
\operatorname{LedgerPolicy}).
$$
It records the histories being related, the relation claimed, the sameness classifier, the proof of anchor stability, and the ledger of observations and transformations used in the comparison.
\end{definition}

\begin{theorem}[Objectivity requires anchor stability]
\label{thm:objectivity-requires-anchor-stability}
If a claim is frame-independent physical content, then it is anchor-stable.
\end{theorem}

\begin{proof}
Frame-independent physical content is stable under changes of observer anchor by \autoref{def:private-frame-independent-content}. Anchor stability is precisely the classifier-equivalent preservation of the claim under such changes.
\end{proof}

\begin{theorem}[Invariants generate relational objectivity]
\label{thm:invariants-generate-relational-objectivity}
If $I(h_i,h_j)$ is an inter-observer invariant over $\mathcal H$, then any claim determined solely by $I$ is relationally objective over $\mathcal H$.
\end{theorem}

\begin{proof}
The invariant is stable under anchor change. A claim determined solely by it is therefore also stable under anchor change. By \autoref{def:relational-objectivity}, such a claim is relationally objective.
\end{proof}

\begin{corollary}[Objectivity is not local certainty]
\label{cor:objectivity-not-local-certainty}
A claim may be certain within one observer history and still fail to be objective over a multi-observer configuration.
\end{corollary}

\begin{proof}
Local certainty concerns one trace. Objectivity requires anchor stability across histories by \autoref{thm:objectivity-requires-anchor-stability}.
\end{proof}

\section{Relational physical content}
\label{sec:relational-physical-content}

\begin{definition}[Local coordinate content]
\label{def:local-coordinate-content}
A quantity $q_i$ is local coordinate content for $h_i$ when it is defined only relative to the local description carried by $h_i$, such as a local time coordinate, chart coordinate, gauge representative, or measurement ordering.
\end{definition}

\begin{definition}[Relational physical content]
\label{def:relational-physical-content}
A quantity $Q$ is relational physical content when it is produced from local coordinate contents by an inter-observer invariant,
$$
Q=I(q_i,q_j),
$$
and is stable under anchor change.
\end{definition}

\begin{definition}[Gauge-like redundancy]
\label{def:gauge-like-redundancy}
A difference between local descriptions is gauge-like redundancy when it changes local coordinate content but preserves all relational physical content. Thus $q_i$ and $q_i'$ are gauge-like equivalent when, for every admissible inter-observer invariant $I$ and compatible $q_j$,
$$
I(q_i,q_j)\sim I(q_i',q_j).
$$
\end{definition}

\begin{theorem}[Local difference requires invariant separation]
\label{thm:local-difference-requires-invariant-separation}
If every admissible inter-observer invariant gives the same value on local descriptions $q_i$ and $q_i'$, then their difference is not a frame-independent physical difference.
\end{theorem}

\begin{proof}
Frame-independent physical content is determined by inter-observer invariants. If all such invariants agree on $q_i$ and $q_i'$, no relationally objective claim separates them. The difference may remain meaningful as local coordinate content, but it is not physical content at the invariant level.
\end{proof}

\begin{corollary}[Coordinate freedom is not empirical ambiguity]
\label{cor:coordinate-freedom-not-empirical-ambiguity}
Different coordinate descriptions may represent the same physical content when they preserve the same inter-observer invariants.
\end{corollary}

\begin{proof}
By \autoref{thm:local-difference-requires-invariant-separation}, local coordinate differences that do not change invariants are not frame-independent physical differences.
\end{proof}

\begin{corollary}[Empirical disagreement requires invariant separation]
\label{cor:empirical-disagreement-requires-invariant-separation}
Two observers genuinely disagree about physical content only when their records cannot be reconciled by an invariant certificate.
\end{corollary}

\begin{proof}
A local mismatch may be coordinate-like or private to one history. It becomes physical disagreement only when an admissible invariant separates the records.
\end{proof}

\section{Local time and synchronization}
\label{sec:local-time-and-synchronization}

\begin{definition}[Local time stream]
\label{def:reality-local-time-stream}
The local time stream of an observer history $h$ is the ordered sequence of continuation steps by which $h$ grows. If
$$
h_0\to h_1\to\cdots\to h_n,
$$
then the local time stream is the finite order encoded by this chain.
\end{definition}

\begin{definition}[Global clock and synchronization certificate]
\label{def:global-clock-synchronization-certificate}
A global clock for $\mathcal H$ is a single ordering object $T$ into which every $h_i\in\mathcal H$ embeds while preserving all relevant local orders and supplying a privileged shared present. A synchronization certificate between $h_i$ and $h_j$ is a finite ledgered construction
$$
\operatorname{SyncCert}(h_i,h_j)
$$
that relates selected local time steps of $h_i$ to selected local time steps of $h_j$. It is a local relation, not a global clock.
\end{definition}

\begin{theorem}[Local time does not imply global time]
\label{thm:local-time-not-global-time}
The existence of local time streams for observer histories does not imply the existence of a global clock for the configuration.
\end{theorem}

\begin{proof}
Each observer history has its own order of continuation. A global clock requires a single ordering object synchronizing all histories and supplying a privileged shared present. No such object follows from the mere existence of local orders. Temporal comparison requires an additional synchronization certificate.
\end{proof}

\begin{corollary}[Temporal comparison is relational]
\label{cor:temporal-comparison-relational}
A temporal comparison between observer histories must be expressed as an inter-observer relation, not as a reading from a global clock.
\end{corollary}

\begin{proof}
By \autoref{thm:local-time-not-global-time}, local time streams do not supply a global clock. Any cross-history temporal comparison must therefore be certified as a relation between histories.
\end{proof}

\begin{corollary}[Simultaneity is certificate-relative]
\label{cor:simultaneity-certificate-relative}
A simultaneity claim between observer histories is meaningful only relative to a synchronization certificate.
\end{corollary}

\begin{proof}
Simultaneity relates local time streams. Since no global clock is assumed, the relation must be supplied by a certificate connecting the relevant local steps.
\end{proof}

\section{Observer-independent constants}
\label{sec:observer-independent-constants}

\begin{definition}[Observer-independent quantity]
\label{def:observer-independent-quantity}
A quantity $Q$ is observer-independent over $\mathcal H$ when, for all $h_i,h_j\in\mathcal H$,
$$
Q^{h_i}\sim Q^{h_j},
$$
where $Q^{h_i}$ denotes the value computed with $h_i$ as anchor.
\end{definition}

\begin{definition}[Maximum relational rate]
\label{def:maximum-relational-rate}
A maximum relational rate $v_{\max}$ is a quantity over a multi-observer configuration such that all admissible cross-history causal dependences are bounded by $v_{\max}$ and $v_{\max}$ is invariant under change of observer anchor. The definition names a structural role and does not assign a numerical value.
\end{definition}

\begin{theorem}[Observer-independent constants are invariants]
\label{thm:observer-independent-constants-invariants}
If a quantity has the same classifier-equivalent value for every observer anchor in a multi-observer configuration, then it is an inter-observer invariant.
\end{theorem}

\begin{proof}
An inter-observer invariant is stable under change of observer anchor. The hypothesis states exactly that changing the anchor preserves the value up to the relevant classifier.
\end{proof}

\begin{corollary}[Invariant maximum rate is frame-independent]
\label{cor:invariant-maximum-rate-frame-independent}
If a maximum relational rate is observer-independent, then it is frame-independent physical content.
\end{corollary}

\begin{proof}
By \autoref{thm:observer-independent-constants-invariants}, observer-independence implies inter-observer invariance. Frame-independent physical content is carried by such invariants.
\end{proof}

\begin{corollary}[Structural form and empirical value are distinct]
\label{cor:structural-form-empirical-value-distinct}
A framework may derive the form of an observer-independent maximum rate without deriving its empirical value.
\end{corollary}

\begin{proof}
The structural form is the invariance of a maximum relational rate under observer-anchor change. Its numerical value requires empirical calibration within a physical theory and observation bundle.
\end{proof}

\section{Tower-aware objectivity}
\label{sec:tower-aware-objectivity}

\begin{definition}[Tower-indexed invariant]
\label{def:tower-indexed-invariant}
For an approximation tower
$$
\mathcal T:L_0\to L_1\to\cdots\to L_n,
$$
a tower-indexed invariant is an inter-observer invariant $I_k$ defined at a specified level $L_k$. It is not automatically valid at other levels.
\end{definition}

\begin{definition}[Cross-level invariant descent]
\label{def:cross-level-invariant-descent}
A tower-indexed invariant $I_j$ at $L_j$ descends to $L_i$, with $i<j$, when a certificate shows that the invariant value at $L_j$ is determined solely by structures preserved from $L_i$. We write
$$
\operatorname{DescInv}_{j\to i}(I_j).
$$
\end{definition}

\begin{theorem}[Invariance is tower-relative without descent]
\label{thm:invariance-tower-relative-without-descent}
Invariance at one approximation level does not automatically imply invariance at another level.
\end{theorem}

\begin{proof}
Each tower level has its own visible structures, classifiers, and hidden residues. An invariant at one level may depend on structures introduced by compression, smoothing, completion, or idealization. Another level may expose distinctions suppressed there or lack structures that the invariant requires. Transfer therefore requires cross-level invariant descent.
\end{proof}

\begin{corollary}[Objectivity is level-relative unless descent is supplied]
\label{cor:objectivity-level-relative-unless-descent}
A physical claim may be objective at one approximation level without yet being objective across the entire tower.
\end{corollary}

\begin{proof}
Objectivity is defined by invariance. By \autoref{thm:invariance-tower-relative-without-descent}, invariance does not automatically move across tower levels.
\end{proof}

\begin{corollary}[Effective objectivity is legitimate but local]
\label{cor:effective-objectivity-legitimate-local}
An effective theory may contain objective quantities within its certified domain even when those quantities are not globally final.
\end{corollary}

\begin{proof}
If a quantity is invariant within the theory's level and continuation domain, it is objective there. The same fact does not supply global descent across all levels.
\end{proof}

\section{Objectivity without finality}
\label{sec:objectivity-without-finality}

\begin{definition}[Objective but open claim]
\label{def:objective-but-open-claim}
A claim $\varphi$ is objective but open when it has an invariant certificate over the currently admissible observer histories and tower level, and it has a specified failure surface under later refinement, added observers, or tower-level change.
\end{definition}

\begin{theorem}[Objectivity does not imply finality]
\label{thm:objectivity-does-not-imply-finality}
If $\varphi$ is relationally objective over $\mathcal H$, it does not follow that $\varphi$ is final over all later configurations, refinements, or observation bundles.
\end{theorem}

\begin{proof}
Relational objectivity over $\mathcal H$ means that $\varphi$ is determined by an inter-observer invariant within that configuration. Later inquiry may extend the configuration, refine the observation bundle, or move to another approximation level. Such changes may expose hidden residues or require new invariant certificates.
\end{proof}

\begin{corollary}[Objectivity is compatible with revisability]
\label{cor:objectivity-compatible-revisability}
A claim may be objectively established relative to current invariants while remaining open to later correction.
\end{corollary}

\begin{proof}
By \autoref{thm:objectivity-does-not-imply-finality}, objectivity does not entail finality. Revisability concerns the possibility that later observations or refinements alter the certified invariant structure.
\end{proof}

\begin{corollary}[Final objectivity would require an oracle]
\label{cor:final-objectivity-requires-oracle}
A claim of final objectivity over all observers, all refinements, and all future histories would require a final-fit oracle or final synchronization oracle.
\end{corollary}

\begin{proof}
Final objectivity would require a certificate covering every possible observer history, observation bundle, tower refinement, and continuation. Such a certificate would function as a global oracle over the total observational process, which the framework rejects.
\end{proof}

\begin{remark}[Compressed form]
\label{rem:objectivity-compressed-form}
The replacement is not
$$
\text{objective truth}
=
\text{truth from nowhere},
$$
but
$$
\text{objective truth}
=
\text{invariant, ledgered, anchor-stable content across observer histories}.
$$
The absence of a privileged observer therefore does not erase objectivity. It requires every objective claim to state the histories related, the classifier under which the relation is evaluated, the invariant that survives anchor change, and the ledger recording how the comparison was made.
\end{remark}
