\chapter{The recursor as an authorized generator}
\label{ch:recursor-as-authorized-generator}

This chapter identifies the host CIC recursor, the eliminator generated for each accepted \texttt{inductive} declaration, as the canonical authorized generator behind BEDC's structural proof practice. The point is not that BEDC adds a new principle to CIC. The point is that BEDC reads the kernel's existing acceptance of \texttt{I.rec} as an authorization event: once the constructor signature is accepted, every legal use of the recursor is a generator action whose output carries a named certificate of membership in the associated closure.

\section{The setup}
\label{sec:recursor-generator-setup}

In Lean 4, an \texttt{inductive} declaration presents a closed constructor signature. The declaration of \texttt{Nat} gives zero and successor; the BEDC declaration of \texttt{BMark} gives \texttt{b0} and \texttt{b1}; the BEDC declaration of \texttt{BHist} gives \texttt{Empty}, \texttt{e0}, and \texttt{e1}; the BEDC.MetaCIC declaration of \texttt{Term} gives \texttt{var}, \texttt{app}, \texttt{lam}, \texttt{pi}, and \texttt{sort}. The corresponding eliminators \texttt{Nat.rec}, \texttt{BMark.rec}, \texttt{BHist.rec}, and \texttt{Term.rec} are not later postulates. They are emitted by the kernel from the accepted constructor signatures.

The associated reading is:
$$
\begin{aligned}
\text{constructor signature accepted}
&\Longrightarrow \text{closed generated carrier},\\
\text{closed generated carrier}
&\Longrightarrow \text{kernel eliminator } I.\text{rec},\\
I.\text{rec}
&\Longrightarrow \text{structural computation over exactly that carrier}.
\end{aligned}
$$

This is the pure paradigm of a closed generator. The carrier has no hidden constructor outside the signature, and the eliminator has no hidden branch outside the constructor cases. For \texttt{Term}, for example, every structurally recursive definition must pay for the five visible cases. For \texttt{BHist}, every proof by cases or induction must pay for the empty case and the two extension cases. BEDC treats this exact finite payment as the operational content of authorization.

\section{The kernel principle}
\label{sec:recursor-generator-kernel-principle}

For each \texttt{inductive} declaration $I$, the Lean kernel emits an elimination principle $I.\text{rec}$. The acceptance criteria are the ordinary kernel criteria for inductive families: the constructor signature must be strictly positive, and recursive uses exposed through definitions and proofs must be structurally decreasing or otherwise accepted by the kernel's termination checker. These criteria are not optional annotations. They are the gate through which the signature becomes a generator.

BEDC reads the gate as follows. Strict positivity prevents a constructor from smuggling a negative self-use that would turn the carrier into an uncontrolled truth device. Structural decrease prevents recursive computation from escaping the constructor spine it claims to consume. Kernel acceptance is therefore the generator's authorization stamp, and rejection is the absence of authorization. No further axiom is injected at the paper layer.

\begin{principle}[Recursor authorization]
\label{prin:recursor-authorization}
Let $I$ be a Lean \texttt{inductive} declaration accepted by the kernel. The emitted eliminator $I.\text{rec}$ is an authorized BEDC generator exactly over the closed carrier generated by $I$'s accepted constructors. A use of $I.\text{rec}$ is authorized only when its motive and branch data are accepted by the kernel and its recursive calls remain inside the structural closure of $I$.
\end{principle}

The host kernel is thus not merely checking a proof after the fact. It is sealing the generator at signature time and checking each generator call at use time. BEDC names this combination generator authorization.

\section{Generator role}
\label{sec:recursor-generator-role}

The operational role of \texttt{I.rec} is to consume a generated $I$-object and produce an output by one branch per constructor. In non-dependent form the output type is fixed. In dependent form the motive may vary over the consumed object. Either way, the generator's closure is the same: every branch is tied to a constructor, and recursive hypotheses are available only for structurally smaller constructor arguments.

For a classifier $C$ over the carrier $I$, the recursor gives the canonical closure pattern:
$$
\begin{aligned}
\text{base branches certify } C \text{ on primitive constructors},\\
\text{step branches transport } C \text{ across constructor extension},\\
\hline
\text{the recursor certifies } C(x) \text{ for every } x:I.
\end{aligned}
$$

The phrase "for every $x:I$" is not a free-floating universal over an ambient totality. It is the generator-internal universal over the closure of the accepted constructor signature. This is the same boundary as \autoref{prin:certificate-closure-structure-internal-all-external}: structural induction is internal to an authorized generator; the move to an unscoped "all" is external.

\section{NameCert structure}
\label{sec:recursor-namecert-structure}

A legal \texttt{I.rec} call produces more than an isolated well-typed term. It produces a term whose well-typedness is backed by the closure of the generator that produced it. In BEDC vocabulary, that output is a \NameCert{} at the relevant name:
$$
\begin{aligned}
\NameCert_{I.\mathrm{rec}(M,\beta,x)}
  &= \text{the named certificate that the recursor output is generated}\\
  &\quad \text{from the accepted } I \text{ signature, motive } M,
        \text{ and branch package } \beta.
\end{aligned}
$$

The certificate is named because the output can be referenced later as a stable proof object or definition. It is a certificate because its well-typedness is not supplied by an external assertion. It is supplied by the recursor's sealed closure: the motive is checked, each branch is checked against its constructor boundary, and the recursive occurrences are accepted only where the kernel can see structural descent.

This is why a \texttt{cases} or \texttt{induction} proof in Lean is not an ad hoc proof script in BEDC's reading. The tactic elaborates to eliminator use. The resulting term is certified because the eliminator is certified. Every such proof object is therefore a named generator output, unless it imports a forbidden external principle through its transitive dependency chain.

\section{Generator-closure classifier view}
\label{sec:recursor-generator-closure-classifier}

Given an accepted inductive $I$, the natural classifier is:
$$
\begin{aligned}
I.\mathsf{WellFormed}(x)
  &:= x \text{ is generated by the accepted constructor signature of } I.
\end{aligned}
$$

Inside Lean this classifier is not usually exposed as a separate predicate for plain inductive objects, because the judgment $x:I$ already carries it. BEDC makes the classifier explicit. The generator is the family of all legal calls to $I.\text{rec}$. The generator-closure statement is:
$$
\begin{aligned}
x:I
\ \wedge\
\texttt{I.rec} \text{ is called with kernel-accepted motive and branches}
\quad \Longrightarrow \quad
I.\mathsf{WellFormed}(\texttt{I.rec}\;x).
\end{aligned}
$$

When the recursor output does not itself have type $I$, the classifier is read at the output type: the output is well formed at its target type because the computation was generated through an authorized eliminator and accepted branch package. Thus the classifier-closure statement is not restricted to endomaps on $I$. It says that recursor-generated outputs remain inside the well-formed fragment of the target judgment selected by the motive.

No axiom appears in this classifier. The closure is the kernel's internal induction over the constructor signature. The audit-relevant object is the generated proof term itself, not an external statement that the proof term should be trusted.

\section{Comparison with classical ``by definition'' reading}
\label{sec:recursor-classical-by-definition}

Classical foundational prose often treats eliminators as available "by definition": once the inductive type is declared, induction and recursion are simply part of what the declaration means. That reading is extensionally correct but hides the authorization event. BEDC keeps the event visible.

In BEDC terms, "by definition" means:
$$
\begin{aligned}
\text{authorized at signature time}
\quad+\quad
\text{sealed at kernel-acceptance time}
\quad+\quad
\text{checked at each eliminator call}.
\end{aligned}
$$

The difference is not a stronger logical assumption. BEDC does not place a deeper metaphysical principle underneath Lean's recursor. It records the operational structure already present in the kernel: strict positivity, constructor closure, structural descent, branch completeness, and type checking of the produced term. Classical prose compresses these into definitional availability. BEDC expands the compression into generator authorization and \NameCert{} output, with the $\mathsf{GAP}$ ledger marking any remaining handoff to the host kernel as a $\mathsf{T}$-socket in the sense of \autoref{prin:certificate-closure-gap-as-T-socket}.

\section{Connection to closed-term substitution}
\label{sec:recursor-closed-term-substitution}

The closed-term substitution lemma in BEDC.MetaCIC gives a direct analogue. The theorem \texttt{substitute\_closed} says that substituting at a closed boundary does not change a closed term:
\leanvariant{BEDC.MetaCIC.substitute\_closed}
The companion \texttt{shift\_closed} theorem has the same closure shape for shifting:
\leanvariant{BEDC.MetaCIC.shift\_closed}
Both are packaged as concrete instances of the generator-closure classifier structure: \leanvariant{BEDC.MetaCIC.GeneratorClosureClassifier} \leanvariant{BEDC.MetaCIC.closed\_under\_shift\_classifier} \leanvariant{BEDC.MetaCIC.closed\_under\_substitute\_classifier}.

The structure is:
$$
\begin{aligned}
\text{classifier} &:= \texttt{ClosedAt}\ d\ t,\\
\text{generator} &:= \texttt{substitute}\ d\ v,\\
\text{closure} &:= \texttt{substitute}\ d\ v\ t = t
  \text{ whenever } \texttt{ClosedAt}\ d\ t.
\end{aligned}
$$

The proof proceeds by structural induction over the \texttt{ClosedAt} certificate. Each branch corresponds to one visible constructor of the classifier: variable, application, lambda, Pi, or sort. The proof is therefore a recursor-generated \NameCert{} for the claim that the substitution generator cannot escape the closed-term classifier.

The \texttt{I.rec} case is the same pattern at the host-CIC level:
$$
\begin{aligned}
\text{closed-term substitution:}\quad
&\texttt{ClosedAt} \text{ classifier closed under } \texttt{substitute},\\
\text{inductive recursor:}\quad
&\texttt{WellTyped} \text{ classifier closed under legal } I.\texttt{rec} \text{ calls}.
\end{aligned}
$$

The two claims are structurally isomorphic. In both cases, a classifier is preserved because the generator is constrained by the same constructor closure that produced the classifier. In both cases, no axiom is appended from outside the proof term.

\section{Audit gate as the executable form of the classifier}
\label{sec:recursor-audit-gate}

The executable form of the generator-closure classifier is the audit gate. Running \texttt{lake build} asks the Lean kernel to re-check every generated proof term: every \texttt{inductive} signature, every emitted or consumed recursor, every branch package, every definitional computation, and every theorem body. If a term depends on an unauthorized generator or fails its classifier, the kernel does not elaborate it.

BEDC adds two visible constraints on top of ordinary build success. The source audit rejects project-level \texttt{axiom} declarations, and the purity audit rejects forbidden transitive dependencies such as \texttt{Classical.choice}, \texttt{Quot.sound}, and \texttt{propext}. These gates make the classifier objective: the paper does not merely claim that recursor outputs stay inside their closure; the build graph and dependency audit decide whether the claim survives execution.

Thus the BEDC pipeline implements:
$$
\begin{aligned}
\texttt{lake build}
&= \text{kernel execution of generator-closure checking},\\
\texttt{check-axioms.py}
&= \text{source-level rejection of axiom backdoors},\\
\texttt{axiom-purity}
&= \text{transitive rejection of forbidden host principles}.
\end{aligned}
$$

Together these gates state that the closure does not leak. A recursor-induced \NameCert{} is accepted only if the kernel can replay the construction and the audit can find no axiom channel behind it.

\section{Boundary: what is not a recursor-induced NameCert}
\label{sec:recursor-boundary-not-induced}

Not every well-typed Lean term is a recursor-induced \NameCert{} in the strict BEDC sense. A proof whose transitive dependencies include \texttt{Classical.choice} imports a choice witness not generated by the relevant inductive closure. A proof depending on \texttt{Quot.sound} imports quotient equality as a host axiom. A proof depending on \texttt{propext} imports propositional extensionality. Such terms may be accepted by a broader Lean environment, but they are not BEDC-authorized generator outputs.

BEDC's project discipline forbids this family. The mathlib-free Lean tree, the no-\texttt{axiom} source gate, and the strict purity audit keep BEDC lemmas inside the recursor-and-constructor fragment. Within that fragment, a public lemma is generated either directly by constructors, by definitions unfolded over constructors, or by recursor use accepted by the kernel. Its certificate is therefore recursor-induced or constructor-induced, and its name is a \NameCert{} rather than an imported classical closure.

This boundary is the practical content of the chapter. The CIC recursor is not an unexamined magic rule inside BEDC. It is the primary authorized generator: accepted by strict positivity, sealed by kernel checking, executed by structural recursion, named by its generated proof term, and audited so that no axiom backdoor can masquerade as closure.

\concretizedIn{ch:concrete-instances-recursorinducednamecert-namecert}{The recursor-as-generator vision is realized as a finite NameCert packet for recursor-induced proof and definition outputs.}
\concretizedIn{ch:concrete-instances-authorizedgeneratorrecursor-namecert}{Authorized generator recursors are realized as finite NameCert packets over accepted constructor signatures, branch coverage, structural descent, and audit provenance.}
\concretizedIn{ch:concrete-instances-recursorgenerator-namecert}{Concrete recursor-generator packet for accepted inductive signatures, legal eliminator calls, audit non-escape, and closed-term handoff.}
\concretizedIn{ch:concrete-instances-recursorauthorization-namecert}{Recursor authorization is realized as a finite NameCert packet for constructor signatures, emitted eliminators, branch packages, and generator non-escape.}
\concretizedIn{ch:concrete-instances-authorizedrecursor-namecert}{Authorized recursor packets realize legal eliminator calls as finite NameCert carriers over constructor signatures, motives, branches, output rows, and audit non-escape ledgers.}
\concretizedIn{ch:concrete-instances-recursion-authorization-ledger-namecert}{Recursion authorization ledgers realize accepted recursor calls as finite BHist packets over signature, motive, branch, descent, output, audit, and non-escape rows.}
