\chapter{The twin substrate architecture: MetaCIC and GroundCompiler}
\label{ch:twin-substrate-synthesis}

\section{The setup}
\label{sec:twin-substrate-synthesis-setup}

BEDC has two main Lean substrates for the self-compilation story.
They are not two presentations of the same module. They answer two
different audit questions.

\texttt{BEDC.MetaCIC} is the closed-CIC meta-theory substrate. Its
subject matter is the formal grammar and proof-theoretic behaviour of a
closed calculus: typing surfaces, beta steps, closedness, substitution,
consistency assembly, subject reduction, normalisation, confluence, and
decidable checking. Its paper-facing synthesis is
\autoref{ch:metacic-audit-synthesis}.

\texttt{BEDC.GroundCompiler} is the self-compilation substrate. Its subject
matter is the compiler-facing route from event flows and source channels to
generated recognisers, certificate gates, metric boundaries, cannot-claim
rows, and streaming compiler discipline. Its paper-facing audit map is
\autoref{ch:bedc-groundcompiler-audit-map}.

The two substrates cooperate in the BEDC roundtrip, but each remains
separately audit-able. MetaCIC records what the closed calculus can and
cannot support. GroundCompiler records what the self-compile pipeline can and
cannot count as generated, encoded, certified, or excluded as hidden input.

\section{Why two substrates}
\label{sec:twin-substrate-synthesis-why-two}

BEDC self-compilation needs two forms of assurance.

The first assurance is meta-theoretic. The project needs a closed substrate in
which reduction, closedness, normalisation, confluence, substitution, and
consistency claims have explicit proof status. This is the work of MetaCIC.
The central question is not whether a compiler report is trustworthy. The
central question is whether the represented closed calculus supports the
meta-theoretic transport steps that the paper wants to use.

The second assurance is compiler-facing. The project needs a pipeline in
which a source-like event stream is encoded, normalised, recognised, packaged,
reported, and gated without importing hidden host structure as formal input.
This is the work of GroundCompiler. The central question is not whether
closed-CIC subject reduction holds. The central question is whether a
compiler-layer artifact is allowed to count as a BEDC input, output,
certificate, report, or non-evidence row.

Keeping these assurances apart makes obstructions visible. MetaCIC has the
dependent-codomain subject-reduction frontier described in
\autoref{ch:metacic-subject-reduction-obstruction}. GroundCompiler has
compiler-pipeline boundaries around conservativity, address analysis,
source-channel separation, certificate mediation, and cannot-claim ledgers.
These are different boundary kinds. A structural boundary in closed CIC is
not the same thing as a self-compile pipeline boundary.

\section{Audit map family per substrate}
\label{sec:twin-substrate-synthesis-audit-families}

\subsection{MetaCIC audit family}
\label{subsec:twin-substrate-synthesis-metacic-family}

The MetaCIC audit family is deliberately granular. The reader is meant to
move among specialised maps rather than treat the substrate as one large
claim. The family contains subject reduction, confluence, normalisation,
substitution, decidability, typed examples, beta, closure preservation, and
consistency assembly sites, with the cross-map reading gathered in
\autoref{ch:metacic-audit-synthesis}.

This granularity reflects the depth of the substrate. A substitution theorem
does not become a subject-reduction theorem. A confluence bridge does not
become closed consistency. A decidable checker does not become a global
decision oracle for every meta-theoretic property. The audit family keeps
these handoffs explicit, and the synthesis chapter records the critical path
without merging the roles.

\subsection{GroundCompiler audit map}
\label{subsec:twin-substrate-synthesis-groundcompiler-family}

GroundCompiler has a single module-level audit map in
\autoref{ch:bedc-groundcompiler-audit-map}. That map inventories the
compiler-facing file groups, the aggregate statement cells, the checked
theorem wrappers, the conditional cells, and the boundary of the
self-compilation claim.

The asymmetry is informative. MetaCIC is the deeper proof-theoretic substrate
and therefore has a finer audit-map family. GroundCompiler is organised as a
pipeline audit surface with a single chapter collecting event-flow, channel,
recogniser, certificate, metric, motif, and bootstrap boundaries. The
difference does not make one substrate more fundamental than the other. It
shows that their audit surfaces have different shapes.

\section{Audit reexport namespaces}
\label{sec:twin-substrate-synthesis-audit-reexports}

\subsection{\texttt{BEDC.MetaCIC.Audit}}
\label{subsec:twin-substrate-synthesis-metacic-audit-namespace}

\texttt{BEDC.MetaCIC.Audit} is the single namespace for MetaCIC
audit-relevant exports. It collects the obstruction theorem, the subject
reduction interfaces, the discharge bundle and setup interfaces, closed-term
operations, closure-preservation facts, partial discharge witnesses, and
counter-witnesses that downstream audit code may need to cite.

The namespace does not change the logical status of any theorem. It is an
addressing layer. Its purpose is to make the MetaCIC audit surface available
from one place while preserving the distinctions recorded by the specialised
paper maps.

\subsection{\texttt{BEDC.GroundCompiler.Audit}}
\label{subsec:twin-substrate-synthesis-groundcompiler-audit-namespace}

\texttt{BEDC.GroundCompiler.Audit} plays the corresponding role for
GroundCompiler. It collects the main statement cells, main theorem witnesses,
input and channel facts, generated-structure and export boundaries, canonical
code and classifier witnesses, metric conservativity, and cannot-claim
registry interfaces.

This namespace gives the compiler substrate the same kind of audit reference
point that MetaCIC has. A downstream reader can point to
\texttt{BEDC.MetaCIC.Audit} for closed-CIC audit content and to
\texttt{BEDC.GroundCompiler.Audit} for self-compile pipeline audit content.
The common shape is intentional: each substrate exposes one namespace for
audit consumption, while each namespace preserves its own subject matter.

\section{The cross-substrate synthesis result}
\label{sec:twin-substrate-synthesis-cross-result}

The BEDC self-compilation roundtrip is a composition of the two substrates,
not a collapse of one into the other. GroundCompiler supplies the
compiler-facing side: a source program is represented through event flow and
channel structure, transformed through generated recognisers and certificate
gates, and recorded as a ledgered artifact with explicit non-input and
non-evidence boundaries.

MetaCIC supplies the meta-theoretic side: the ledgered artifact is read
against a closed calculus whose reduction, closedness, substitution,
normalisation, confluence, decidability, and consistency interfaces have
their own audit status. A compiler ledger step is therefore not accepted just
because it is textually present. It must be located in the corresponding
MetaCIC legality story when the step claims closed-CIC content.

The synthesis claim is architectural: project-level audit cleanliness requires
both maps to be clean in their own sense. GroundCompiler must not smuggle
hidden compiler input or promote reports into proof evidence. MetaCIC must not
pretend that a blocked closed-CIC transport edge has been supplied. The BEDC
roundtrip is credible only when both refusals hold at the same time.

\section{Apophatic framing of the twin substrate}
\label{sec:twin-substrate-synthesis-apophatic}

This architecture follows the naming discipline of
\autoref{ch:visions-apophatic-naming-as-discipline}. A substrate boundary is
not left anonymous. It is named, routed to the proper audit map, and kept out
of neighbouring claims.

For MetaCIC, the named boundary is the subject-reduction frontier in the
dependent-codomain setting. The paper can discuss closed-normal consistency,
candidate-mediated normalisation, substitution facts, and conditional
transport paths without pretending that the missing closed arbitrary-proof
transport is available.

For GroundCompiler, the named boundaries are compiler-pipeline boundaries:
global conservativity, address analysis, source-channel separation,
certificate-mediated export, metric non-evidence, motif non-evidence, and
cannot-claim registry adequacy. These names stop the self-compile story from
converting code, reports, motifs, or host structure into proof content by
prose.

The twin substrate architecture is therefore apophatic in a project-level
sense. Each substrate says what it can use, what it cannot use, and where the
next required supply would have to appear. The two sets of names are not
interchangeable.

\section{Why not collapse into one substrate}
\label{sec:twin-substrate-synthesis-no-collapse}

Collapsing MetaCIC and GroundCompiler into one substrate would blur two audit
gates that need different questions. A closed-CIC structural property asks
about terms, reduction, closedness, binders, typing surfaces, and normal
forms. A compiler-pipeline property asks about source channels, encodings,
recognisers, generated structure, certificates, reports, ledgers, and hidden
input.

The distinction matters for reuse. A downstream formalisation that needs
closed substitution or closed-normal consistency should cite the MetaCIC
surface. A downstream compiler audit that needs channel losslessness,
certificate-mediated export, or metric conservativity should cite the
GroundCompiler surface. A chapter that needs the full self-compilation
roundtrip must say where each half of the claim is discharged.

The split also prevents category mistakes. A theorem saying code is not proof
does not solve subject reduction. A theorem about closed substitution does not
prove that a compiler report is a certificate. A confluence bridge does not
make a hidden compiler input visible. A channel bijection does not establish
closed-CIC consistency. The architecture keeps these refusals local and
auditable.

\section{Boundary}
\label{sec:twin-substrate-synthesis-boundary}

This chapter is an architecture description. It is not a proof attempt for
the remaining MetaCIC frontier, and it is not a claim that the compiler
pipeline alone completes BEDC self-compilation.

The allowed reading is narrower and stronger. BEDC has two cooperating
substrates for the roundtrip. MetaCIC carries the closed-CIC meta-theory audit
surface. GroundCompiler carries the self-compile pipeline audit surface. Their
audit namespaces provide parallel reference points, and their paper maps
record distinct boundary kinds. The project-level self-compilation story
depends on both, while neither is allowed to impersonate the other.

\concretizedIn{ch:concrete-instances-twinsubstrateroundtrip-namecert}{The cross-substrate roundtrip is represented as a finite NameCert packet separating MetaCIC audit rows from GroundCompiler audit rows.}

\concretizedIn{ch:concrete-instances-twin-substrate-audit-packet-namecert}{TwinSubstrateAuditPacket records the MetaCIC and GroundCompiler audit routes as one finite NameCert packet with separate non-escape ledgers.}

\concretizedIn{ch:concrete-instances-twinsubstratesynthesis-namecert}{The twin-substrate architecture is concretized as a finite cross-substrate audit packet.}
\concretizedIn{ch:concrete-instances-twin-substrate-audit-namecert}{The twin-substrate audit packet records the MetaCIC and GroundCompiler handoff as one finite NameCert surface without collapsing their audit roles.}
