\subsection{Total audit theory}
\label{subsec:philosophy-total-audit}

\begin{definition}[Admissible claim]
\label{def:philosophy-admissible-claim-total}
A claim is admissible when it has carrier, classifier, ledger, status,
certificate or gap or cannot-claim surface, and no-leakage discipline.
\end{definition}

\begin{definition}[Failure certificate]
\label{def:philosophy-failure-certificate-total}
A failure certificate is the negative certificate of a claim: it states
which required field is missing, invalid, overstated, unchecked, or
confused across the theory-closure and formal-verification axes.
\end{definition}

\begin{theorem}[Positive and negative certificates]
\label{thm:philosophy-positive-negative-certificates-total}
Certificates license export, failure certificates block export, and
cannot-claim entries record refusal.
\end{theorem}
\begin{proof}
The positive certificate fills source, classifier, exactness, ledger,
stability, bridge, and status fields. The failure certificate names a
missing or invalid field. The cannot-claim entry records that the
manuscript does not make the adjacent claim at the current surface.
\end{proof}

\begin{corollary}[Cannot-claim is negative knowledge]
\label{cor:philosophy-cannot-claim-negative-knowledge-total}
The cannot-claim registry is part of BEDC's philosophical structure,
not a modesty convention.
\end{corollary}
\begin{proof}
The registry records typed refusals and required upgrades. It is the
negative face of the export surface.
\end{proof}

\subsection{Total system diagram}
\label{subsec:philosophy-total-system-diagram}

\begin{definition}[Three-layer system]
\label{def:philosophy-three-layer-system-total}
The BEDC philosophical system has three layers. The ground layer
contains \(\bzero,\bone\), marks, histories, \(\msame\), \(\hsame\),
extension, and continuation. The certificate layer contains asking,
signatures, packages, gaps, naming certificates, semantic naming
certificates, derivation certificates, and standard bridges. The
boundary and interpretation layer contains gaps, the far-end position,
conscious records, universe slices, scientific objects, tradition
maps, and audit methods.
\end{definition}

\begin{definition}[Generation, naming, boundary]
\label{def:philosophy-generation-naming-boundary-total}
The whole framework can be compressed into three questions: generation
asks how a thing is produced, naming asks how it stabilizes as an
object, and boundary asks why it cannot be closed internally.
\end{definition}

\begin{theorem}[Three-question synthesis]
\label{thm:philosophy-three-question-synthesis}
Every BEDC philosophical question falls under generation, naming, or
boundary.
\end{theorem}
\begin{proof}
Objects, knowledge, subjectivity, time, consciousness, universe,
science, and philosophical comparison all require a carrier, a
classifier or naming certificate, and an account of any unclosed
commitment. Those are exactly the generation, naming, and boundary
questions.
\end{proof}

\begin{corollary}[BEDC question form]
\label{cor:philosophy-bedc-question-form-total}
Given a concept \(X\), BEDC first asks for its carrier, classifier,
ledger, naming certificate, gap surface, and status.
\end{corollary}

\subsection{Auditable-generativity theorem}
\label{subsec:philosophy-auditable-generativity-theorem}

\begin{theorem}[Auditable generativity]
\label{thm:philosophy-auditable-generativity-total}
The complete BEDC philosophical framework is auditable generativity:
distinction-grounded, history-carried, continuation-dynamic,
name-certificate-licensed, ledger-tracked, gap-bounded,
bridge-conservative, and audit-governed.
\end{theorem}
\begin{proof}
Distinction precedes information, and histories are the minimal
information carriers. Observation and time are read through
continuation, and observer is history. Objects and knowledge require
naming certificates and witnesses. Logic admits explicit construction
and local refutation while refusing meta closure. Commitments beyond
closed generation are exposed as gaps and far-end positions.
Consciousness, universe, space, causality, freedom, other minds, and
self-reference are rewritten as records-side carriers or sockets.
Scientific objects require records, invariants, empirical ledgers, and
bridges. Philosophical traditions enter only through structural maps.
Audit methodology requires every claim to report carrier, classifier,
ledger, status, and refusal surface. These results together give
auditable generativity.
\end{proof}

\begin{corollary}[One-sentence characterization]
\label{cor:philosophy-one-sentence-characterization}
BEDC is an auditable generative system that starts from primitive
distinction, generates histories and continuations, licenses names by
certificates, keeps boundaries open through gaps and the far-end
position, and governs export strength by audit gates.
\end{corollary}

\begin{corollary}[Negative characterization]
\label{cor:philosophy-negative-characterization-total}
BEDC is not traditional realism, subjectivist idealism, ordinary
formalism, naive constructivism, psychologistic phenomenology, global
physical realism, theological object theory, or a host-theory import
system. It is distinction ontology, history generativity, observerless
observation theory, certificate object theory, witness epistemology,
open-meta boundary theory, gap and far-end transcendence theory,
relational science theory, and audit writing theory.
\end{corollary}

\begin{corollary}[Research programme]
\label{cor:philosophy-research-programme-total}
Further work should proceed by the lowest open layer: finite kernel,
finite data certificates, arithmetic certificates, algebra
certificates, order and logic certificates, set-like and type-like
interfaces, topology and metric completion, analysis, geometry,
category theory, homology, number theory, spectra, and mature-system
bridges.
\end{corollary}

\subsection{Status record}
\label{subsec:philosophy-final-status-record}

\begin{definition}[Philosophy package status]
\label{def:philosophy-package-status-record}
The philosophy package is a paper-level structural reading of the BEDC
kernel and certificate architecture. It introduces no kernel
primitive. It is closed as a scoped synthesis of primitive distinction,
history, continuation, naming certificates, gap and far-end boundary
theory, standard bridge discipline, and audit gates. It does not close
full physical theory, empirical constants, complete arithmetic
reconstruction, real completion, a global truth predicate, internal
runtime validation, or phenomenal consciousness as object-level
essence. It makes no whole-package Lean target claim; component
targets belong to their cited kernel, naming-certificate, bridge, and
audit chapters.
\end{definition}

\begin{corollary}[Upgrade path]
\label{cor:philosophy-package-upgrade-path}
To promote the philosophy package from paper-level synthesis to a
formal package, one would define a formal structure for philosophy
maps, encode tradition maps, gap reports, and writing items, check
no-host-leak and no-meta-closure dependencies, and give a finite
theorem list for each mapped concept.
\end{corollary}
