\subsection{Total definition}
\label{subsec:philosophy-total-definition}

\begin{definition}[BEDC philosophy]
\label{def:philosophy-bedc-philosophy}
BEDC philosophy is the structural theory of what can be generated, what
can be named, what can be known, what must remain open, and what may be
exported. Its basic terms are not substances, minds, worlds, or laws,
but carriers, classifiers, witnesses, ledgers, certificates, gaps,
bridges, and audit gates.
\end{definition}

\begin{definition}[Auditable generativity]
\label{def:philosophy-auditable-generativity-total}
Auditable generativity is the thesis that every admissible object,
knowledge claim, scientific claim, philosophical reading, or bridge
claim must be generated, classified, ledgered, certified, or explicitly
marked as a gap or cannot-claim entry.
\end{definition}

\begin{definition}[Auditable generation chain]
\label{def:philosophy-auditable-generation-chain}
The auditable generation chain is the route
$$
\begin{gathered}
\bzero,\bone
\to \mathsf{MarkSameness}/\mathsf{NoConfusion}
\to \Hist
\to \hsame
\to \mathsf{Ext}/\Cont
\to \mathsf{Ask}/\mathsf{Sig}/\mathsf{sameSig}
\to \mathsf{Pkg}/\Gap
\to \NameCert
\to \mathsf{DerivCert}/\mathsf{ClosureStatus}/\mathsf{FormalStatus}
\to \mathsf{StandardBridge}\ \text{or}\ \mathsf{CannotClaim}.
\end{gathered}
$$
Completion-like, fold-like, geometric, algebraic, scientific, and
philosophical interfaces enter through their own certificate schemas,
not as kernel primitives.
\end{definition}

\begin{theorem}[Generation-chain priority]
\label{thm:philosophy-generation-chain-priority}
Every mature BEDC concept must occupy a position in the auditable
generation chain.
\end{theorem}
\begin{proof}
A concept without a generation-chain position has no carrier. Without
a carrier it has no classifier. Without a classifier it has no
auditable account of sameness, difference, transport, or exactness.
Without a ledger, any compression or hidden material is untraceable.
Without a certificate, the concept is not a licensed name. Hence
mature concepts must be located in the chain.
\end{proof}

\begin{corollary}[No position, no export]
\label{cor:philosophy-no-position-no-export}
If a concept cannot state its carrier, classifier, ledger, and status,
it cannot be exported as a BEDC object.
\end{corollary}
\begin{proof}
The missing fields are precisely the fields by which the generation
chain becomes auditable. The concept may remain a reading, gap,
roadmap, or cannot-claim entry, but it is not an export.
\end{proof}

\subsection{Total ontology}
\label{subsec:philosophy-total-ontology}

\begin{definition}[BEDC existence]
\label{def:philosophy-bedc-existence}
At the object layer, \(X\) exists in BEDC when \(X\) has a licensed
carrier, classifier, ledger, and certificate position. Mature existence
is the conjunction of a naming certificate and the relevant reported
status.
\end{definition}

\begin{definition}[Licensed object]
\label{def:philosophy-licensed-object-total}
A licensed object is an interface whose naming certificate supplies
source specification, pattern specification, classifier specification,
stability certificate, and ledger policy.
\end{definition}

\begin{theorem}[Mature existence is naming license]
\label{thm:philosophy-mature-existence-naming-license}
In the mature object layer, to exist is to have licensed naming status.
\end{theorem}
\begin{proof}
A mature object cannot be introduced as a bare kernel primitive. It
therefore enters through a \(\NameCert\) and the associated status
record. Conversely, a name with those fields is available as a licensed
interface at its stated scope. Thus mature existence is naming license.
\end{proof}

\begin{corollary}[Anti-substance ontology]
\label{cor:philosophy-anti-substance-ontology}
BEDC does not read the world as a collection of substances, but as a
stratified field of licensed generated interfaces.
\end{corollary}
\begin{proof}
Substance ontology places objects before certificates. BEDC licenses
objects only after generation, classification, ledgering, and naming.
\end{proof}

\begin{corollary}[Mature objects are not inputs]
\label{cor:philosophy-mature-objects-not-inputs}
Numbers, reals, sets, functions, limits, topological spaces,
categories, universes, consciousness, causality, freedom, truth, and
God are not BEDC primitives. They can enter only as certificates,
records-side readings, bridge targets, gap positions, or refusal
entries.
\end{corollary}
\begin{proof}
Each item requires structure beyond the primitive distinction and
history constructors. Treating any of them as an input bypasses
carrier, classifier, ledger, certificate, or gap discipline.
\end{proof}

\subsection{Total epistemology}
\label{subsec:philosophy-total-epistemology}

\begin{definition}[BEDC knowledge]
\label{def:philosophy-bedc-knowledge-total}
To know \(P\) in BEDC is to hold an auditable witness for \(P\). Such a
witness may be a sameness witness, continuation witness, classifier
witness, package or gap witness, naming certificate, semantic naming
certificate, derivation certificate, bridge witness, gap report, or
failure certificate.
\end{definition}

\begin{definition}[Knowledge strength]
\label{def:philosophy-knowledge-strength-total}
A knowledge claim reports its strength: seed, obligation, paper-level
closure, checked theorem, checked bridge, gap, or cannot-claim status.
The theory-closure and formal-verification axes remain distinct.
\end{definition}

\begin{theorem}[Knowledge is not bare truth]
\label{thm:philosophy-knowledge-not-bare-truth-total}
BEDC knowledge is possession of a certificate-bearing witness, not
possession of a bare internal truth predicate.
\end{theorem}
\begin{proof}
An internal total truth predicate would close the meta loop. BEDC
keeps the meta loop open. Hence knowledge cannot be defined as access
to such a predicate; it is reported as local witness, certificate,
ledger, bridge, or gap surface.
\end{proof}

\begin{corollary}[To know is to audit]
\label{cor:philosophy-to-know-is-to-audit}
Within BEDC, to know is to be able to audit the witness path.
\end{corollary}
\begin{proof}
Without an auditable path, the claim has no visible source,
classifier, stability, hidden-material ledger, or strength.
\end{proof}
