\subsection{Total observation theory}
\label{subsec:philosophy-total-observation}

\begin{definition}[Observation]
\label{def:philosophy-observation-total}
An observation is a continuation row:
$$
\mathsf{Observation}(h,d,h') := \Cont(h,d,h').
$$
\end{definition}

\begin{definition}[Observer]
\label{def:philosophy-observer-total}
An observer is a history, read modulo \(\hsame\):
$$
\mathsf{Observer}(h) := h : \Hist.
$$
\end{definition}

\begin{definition}[Time]
\label{def:philosophy-time-total}
Time is the local continuation chain by which a history is generated
from the empty history.
\end{definition}

\begin{theorem}[Observation, distinction, and time]
\label{thm:philosophy-observation-distinction-time-total}
At the kernel layer, observation, distinction step, and time step have
the same continuation shape.
\end{theorem}
\begin{proof}
Observation is \(\Cont\) on histories. A distinction step is the
application of the two elementary extension shapes. Local time is the
ordered growth of a history by those steps. These readings share the
same carrier, continuation laws, and \(\hsame\)-respecting behavior.
\end{proof}

\begin{theorem}[Observer is history]
\label{thm:philosophy-observer-is-history-total}
BEDC has no observer-substance behind the history. The observer is the
\(\Hist\) value read under \(\hsame\).
\end{theorem}
\begin{proof}
The continuation signature has no separate subject parameter. Identity
is supplied by \(\hsame\) on histories. Adding a hidden observer entity
would require unlicensed transport between that entity and the visible
history, which is not part of the kernel surface.
\end{proof}

\begin{corollary}[Subject is not substance]
\label{cor:philosophy-subject-not-substance-total}
The subject is a stable reading of the historical trace, not an owner
behind it.
\end{corollary}
\begin{proof}
There is no additional carrier for such an owner. Subject talk is
therefore a reading of history, continuity, and self-proxy ledgers.
\end{proof}

\subsection{Total logic}
\label{subsec:philosophy-total-logic}

\begin{definition}[Allowed proof]
\label{def:philosophy-allowed-proof-total}
An allowed BEDC proof is an explicit witness construction or a local
refutation inside a fixed carrier, classifier, and certificate.
\end{definition}

\begin{definition}[Forbidden proof]
\label{def:philosophy-forbidden-proof-total}
A forbidden proof extracts positive content without constructor
witness, or closes a global truth, choice, quotient, propositional
extensionality, or halting surface.
\end{definition}

\begin{theorem}[Logic discipline synthesis]
\label{thm:philosophy-logic-discipline-total}
BEDC logic is governed by three rules: positive content must be
constructed, negative content must remain local, and the meta loop must
remain open.
\end{theorem}
\begin{proof}
Positive claims require witnesses. Refutations are licensed only inside
fixed certificate surfaces where the carrier, classifier, and closure
laws are displayed. A proof principle that decides all certificates or
all propositions would internalize the meta level and violate the open
meta-loop boundary.
\end{proof}

\begin{corollary}[Classical shortcuts share one refusal]
\label{cor:philosophy-classical-shortcuts-one-refusal}
Choice, quotient collapse, and propositional extensionality are refused
as public BEDC resources because each accepts unwitnessed supply at a
different level.
\end{corollary}
\begin{proof}
Choice supplies a term, quotient collapse supplies an identity, and
propositional extensionality supplies a rewrite principle without the
transport witnesses BEDC requires at the public surface.
\end{proof}

\begin{corollary}[Halting obstruction]
\label{cor:philosophy-halting-obstruction-total}
A total halting predicate for all certificate-level continuations is
the recursion-theoretic face of the same boundary.
\end{corollary}
\begin{proof}
Such a predicate would decide all continuation behavior at the
certificate stratum and thereby close the meta loop that BEDC keeps
open.
\end{proof}

\concretizedIn{ch:concrete-instances-allowed-proof-audit-namecert}{The allowed/forbidden proof boundary is realized as the finite AllowedProofAuditUp NameCert packet.}

\subsection{Total boundary theory}
\label{subsec:philosophy-total-boundary}

\begin{definition}[Closed ground loop]
\label{def:philosophy-closed-ground-loop-total}
The ground loop is closed by the primitive two-constructor distinction.
\end{definition}

\begin{definition}[Open meta loop]
\label{def:philosophy-open-meta-loop-total}
The meta loop is open because BEDC does not internally define its own
total truth predicate, runtime validator, or halting oracle.
\end{definition}

\begin{theorem}[Two-loop synthesis]
\label{thm:philosophy-two-loop-synthesis-total}
BEDC requires closed ground and open meta.
\end{theorem}
\begin{proof}
Without a closed ground, the system cannot start. With a closed meta
loop, the system would validate its own truth or runtime surface from
inside, producing the familiar self-reference obstruction. The loops
therefore have different statuses.
\end{proof}

\begin{corollary}[Minimal ground contribution]
\label{cor:philosophy-minimal-ground-contribution}
BEDC does not bypass formal limits. It compresses the unavoidable
ground loop to primitive distinction and refuses meta closure.
\end{corollary}

\subsection{Total gap and far-end theory}
\label{subsec:philosophy-total-gap-far-end}

\begin{definition}[Gap]
\label{def:philosophy-gap-total}
A gap is a site in a closed system where a requested supply cannot be
discharged internally:
$$
\mathsf{GAP}(\mathsf{Site},\mathsf{RequestedSupply},
\mathsf{SocketType},\mathsf{Gate}).
$$
\end{definition}

\begin{definition}[Far-end position]
\label{def:philosophy-far-end-position-total}
The far-end position \(T\) is the structural position of the supply
requested by gap sockets. It is not an object-layer entity, axiom, or
theorem.
\end{definition}

\begin{theorem}[Gap and far-end synthesis]
\label{thm:philosophy-gap-far-end-synthesis-total}
Every commitment beyond closed records and closed generation must be
exposed as a gap, and the far end of such sockets is named \(T\).
\end{theorem}
\begin{proof}
Finite records cannot yield unrestricted universal closure, unwitnessed
witnesses, external identity, future causal persistence, inter-history
coordination, inscription novelty, or total self-reference closure.
These demands must be reported as sockets rather than internal rules.
\end{proof}

\begin{corollary}[Far end is not object]
\label{cor:philosophy-far-end-not-object-total}
The far-end position can be named only positionally, not reified as an
object.
\end{corollary}
\begin{proof}
If \(T\) were an object, it would need a carrier, classifier, ledger,
and naming certificate. Its role is precisely to mark a supply that the
object layer cannot internalize.
\end{proof}
