\subsection{Total phenomenology}
\label{subsec:philosophy-total-phenomenology}

\begin{definition}[Conscious record]
\label{def:philosophy-conscious-record-total}
A conscious record is the focused records-side packet
$$
\mathsf{ConsciousRecord}(L_N,F) := (H(F),T(F),S(F),\rho).
$$
\end{definition}

\begin{definition}[Universe slice]
\label{def:philosophy-universe-slice-total}
\(\mathsf{Universe}_{L_N}\) is the finite observation-history slice
admitted by the focused ledger \(L_N\).
\end{definition}

\begin{definition}[Space reading]
\label{def:philosophy-space-reading-total}
\(\mathsf{Space}_{L_N}\) is the locality-cell graph together with the
inter-history invariant rows available at the focused ledger.
\end{definition}

\begin{theorem}[Phenomenology synthesis]
\label{thm:philosophy-phenomenology-synthesis-total}
BEDC phenomenology reads consciousness as a focused records-side
carrier, universe as a finite observation-history slice, time as a
local continuation chain, space as inter-history locality geometry,
identity as an \(\hsame\)-stable trace, causality as a Type IV gap,
freedom as a Type VI inscription-event aspect, other minds as Type V
gaps, and self-reference as a Type VII gap-on-gap hierarchy.
\end{theorem}
\begin{proof}
Observer is history and observation is continuation. Hence
consciousness cannot enter as an independent substance. No global
clock or global container is supplied by the kernel, so universe and
space are read from finite slices and inter-history relations.
Causality, freedom, other minds, and self-reference each request a
supply beyond closed records, and so take socket form.
\end{proof}

\begin{corollary}[Hard problem as audit question]
\label{cor:philosophy-hard-problem-audit-question-total}
BEDC does not ask for consciousness as an essence. It asks which
records-side carrier, ledger, self-proxy, relation row, and gap sockets
make consciousness-talk admissible.
\end{corollary}
\begin{proof}
Only records, certificates, and socketed boundary reports can enter the
object layer. Phenomenal excess that lacks those surfaces remains a
gap or reading.
\end{proof}

\subsection{Total philosophy of science}
\label{subsec:philosophy-total-science}

\begin{definition}[Scientific object]
\label{def:philosophy-scientific-object-total}
A scientific object is a certificate package containing a naming
certificate, derivation or closure status, empirical ledger,
inter-history invariant surface, gap report, and optional standard
bridge.
\end{definition}

\begin{definition}[Physical law]
\label{def:philosophy-physical-law-total}
A physical law is an empirical regularity together with a Type IV gap
for future persistence.
\end{definition}

\begin{theorem}[Scientific object synthesis]
\label{thm:philosophy-scientific-object-synthesis-total}
Scientific objects are composites of records, invariants,
certificates, empirical ledgers, bridges, and gap reports; they are not
primitives.
\end{theorem}
\begin{proof}
A scientific object names a pattern in records, classifies and
stabilizes it across perspectives, connects it to measurement and
error ledgers, may compare it with mature model systems, and often
commits to future predictions. Each component carries its own audit
obligation.
\end{proof}

\begin{corollary}[Relational physics principle]
\label{cor:philosophy-relational-physics-principle-total}
Frame-independent physical content is inter-history invariant content.
\end{corollary}
\begin{proof}
Multiple histories have no shared base history, no shared time-step
indexing, and no global synchronization. What survives as physical
content must therefore be carried by stable inter-history relations.
\end{proof}

\begin{corollary}[Model is not world]
\label{cor:philosophy-model-not-world-total}
A model is an interpretation, compression, or bridge for records and
invariants. It is not the world itself.
\end{corollary}
\begin{proof}
The universe available to BEDC is a finite observation-history slice.
Identifying a model with the world would replace that slice by a
global object.
\end{proof}

\concretizedIn{ch:concrete-instances-phenomenology-science-interface-namecert}{The phenomenology/science interface is realized as a finite composite NameCert packet joining records-side consciousness, universe slices, inter-history invariants, empirical ledgers, gap reports, and conservative bridge rows.}

\subsection{Total bridge theory}
\label{subsec:philosophy-total-bridge}

\begin{definition}[Standard bridge]
\label{def:philosophy-standard-bridge-total}
A standard bridge from \(N\) to a host theory \(T\) contains encoding,
decoding, return witnesses in both directions, finite theorem
preservation, and no-host-leak.
\end{definition}

\begin{definition}[Conservative bridge]
\label{def:philosophy-conservative-bridge-total}
A bridge is conservative when it does not inject host primitives into
the BEDC public surface.
\end{definition}

\begin{theorem}[Bridge is not fusion]
\label{thm:philosophy-bridge-not-fusion-total}
A standard bridge is conservative recognition, not fusion with the host
theory.
\end{theorem}
\begin{proof}
The bridge lets a host reader recognize a BEDC object and lets BEDC
accept only the finitely listed translated theorem rows. No-host-leak
blocks host primitives such as host natural numbers, quotient
collapses, choice, propositional extensionality, and host equality
from becoming BEDC inputs.
\end{proof}

\begin{corollary}[Mature systems are bridge targets]
\label{cor:philosophy-mature-systems-bridge-targets-total}
Mature mathematics and mature physics may serve as bridge targets, but
they cannot replace internal BEDC certificates.
\end{corollary}
\begin{proof}
Replacing the certificate by the host theory would turn a bridge into
primitive import and violate no-host-leak.
\end{proof}
