\section{Carrier definition}
\label{sec:numfield-carrier}

\begin{definition}[Reflexive rational field-extension carrier for NumFieldUp]
\label{def:numfield-reflexive-rational-field-extension-carrier}
\label{def:numfield-rat-reflexive-carrier}
The concrete $\NumFieldUp$ carrier is the RatUp reflexive field-extension
carrier of \autoref{def:fieldext-reflexive-extension-carrier}, read as a
number-field certificate surface. Its base carrier and ambient carrier are
both $\mathsf{RatHistoryCarrier}$, its base and ambient classifiers are both
$\mathsf{RatHistoryClassifier}$, and its field-operation table is the concrete
$\FieldUp(\RatUp)$ operation table recorded in the RatUp certificate chapter.

The embedding row is the identity embedding
$$
\iota_{\mathsf{Rat}}:\RatUp\hookrightarrow\RatUp ,
$$
and the finite-degree row is the singleton unary basis row. Thus the displayed
module basis has one vector, the coordinate readback is the RatUp endpoint
itself, and the scalar-action row is RatUp multiplication. The carrier has no
separate algebraic endpoint outside the $\mathsf{BHist}$ rows already used by
the RatUp and FieldExtUp certificates.
\end{definition}
\leandef{BEDC.Derived.NumFieldUp.NumFieldReflexiveRationalCarrier}
\leandef{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveCarrier}

\begin{theorem}[RatUp reflexive NumField carrier and classifier]
\label{thm:numfield-reflexive-carrier-classifier}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the
$\NumFieldUp$ carrier is exactly $\mathsf{RatHistoryCarrier}$ and the
$\NumFieldUp$ endpoint classifier is exactly $\mathsf{RatHistoryClassifier}$.
Every displayed number-field endpoint is therefore a RatUp history endpoint,
and every endpoint comparison is a RatUp classifier comparison.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_carrier\_classifier}
\begin{proof}
Unfold \autoref{def:numfield-reflexive-rational-field-extension-carrier}. The
carrier and classifier fields are specified directly as
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$.

The RatUp semantic name certificate supplies the carried-history
interpretation for these fields. No quotient, completion, polynomial carrier,
or new endpoint classifier is introduced by the $\NumFieldUp$ reading, so each
number-field endpoint is read through the same RatUp history row.
\end{proof}

\begin{theorem}[RatUp reflexive FieldExt consumption for NumFieldUp]
\label{thm:numfield-reflexive-fieldext-consumption}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the
finite-extension component consumed by $\NumFieldUp$ is the identity
$\FieldExtUp$ row of \autoref{def:fieldext-reflexive-extension-carrier}. Its
base field and ambient field are both the concrete $\FieldUp(\RatUp)$
certificate, its embedding is $\iota_{\mathsf{Rat}}(h):=h$, and its scalar
action is the RatUp multiplication row.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_fieldext\_consumption}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_fieldext\_consumption}
\begin{proof}
Read the finite-extension witness from
\autoref{thm:fieldext-reflexive-public-namecert-interface}. That theorem
exposes the public $\FieldExtUp$ interface whose carrier, classifier, base
field, ambient field, identity embedding, self-vector-space rows, exactness,
and ledger all live over the RatUp operation table.

The $\NumFieldUp$ source only consumes that interface. Because the consumed row
is the identity extension, the base and ambient field certificates are the same
RatUp field certificate, and the scalar-action row is the same multiplication
row already present in $\FieldUp(\RatUp)$.
\end{proof}

\begin{theorem}[RatUp reflexive NumField ledger exactness]
\label{thm:numfield-reflexive-ledger-exactness}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the
$\NumFieldUp$ exactness and ledger rows are inherited from the RatUp reflexive
$\FieldExtUp$ public interface. In particular, every carrier display,
classifier display, field-operation endpoint, identity-embedding endpoint,
vector-space endpoint, scalar-action endpoint, and ledger provenance row is one
of the rows listed by
\autoref{thm:fieldext-reflexive-public-namecert-interface}.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:numfield-reflexive-fieldext-consumption}. It identifies the
finite-extension component used by $\NumFieldUp$ with the public RatUp
reflexive $\FieldExtUp$ interface.

Next read the exactness and ledger clauses from
\autoref{thm:fieldext-reflexive-public-namecert-interface}. Its public surface
includes exact endpoint classification and ledger provenance over the RatUp
operation table. Since the carrier and classifier are unchanged by
\autoref{thm:numfield-reflexive-carrier-classifier}, those clauses serve as the
displayed $\NumFieldUp$ exactness and ledger rows without any additional
transport.
\end{proof}

\begin{theorem}[RatUp reflexive NumField NameCert obligation surface]
\label{thm:numfield-reflexive-namecert-obligation-surface}
The carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier} assembles the
paper-side $\NameCert_{\NumFieldUp}$ obligation surface. The surface records
the RatUp history carrier, the RatUp history classifier, the identity
finite-extension witness, the inherited FieldExt stability rows, the inherited
exact endpoint classification, and the inherited ledger provenance from the
RatUp reflexive $\FieldExtUp$ public interface.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_semantic\_name\_certificate}
\begin{proof}
Use \autoref{thm:numfield-reflexive-carrier-classifier} for the carrier and
classifier slots. These slots are the RatUp history carrier and classifier, so
the $\NumFieldUp$ source is rooted in $\mathsf{BHist}$.

Use \autoref{thm:numfield-reflexive-fieldext-consumption} for the finite
field-extension slot. It supplies the identity embedding, the shared
base-and-ambient RatUp field certificates, and the self-vector-space row
required by the number-field reading.

Use \autoref{thm:numfield-reflexive-ledger-exactness} for the exactness and
ledger slots. Together these three rows cover the carrier, classifier,
finite-extension, stability, exactness, and ledger obligations named by the
paper-side $\NameCert_{\NumFieldUp}$ surface.
\end{proof}
