\section{The certificate}
\label{sec:numfield-certificate}

\begin{theorem}[NumFieldUp reflexive rational source scope]
\label{thm:numfield-reflexive-rational-source-scope}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, every
source, carrier, classifier, stability, ledger, exactness, and absent standard
bridge field of the paper-side $\NumFieldUp$ surface is fixed by the displayed
RatUp and FieldExtUp rows. The source is the concrete RatUp $\FieldUp$ table,
the carrier is $\mathsf{RatHistoryCarrier}$, the classifier is
$\mathsf{RatHistoryClassifier}$, stability is the identity-embedding and
self-vector-space stability of the reflexive FieldExtUp row, exactness is
endpoint classification by $\mathsf{RatHistoryClassifier}$, the ledger is the
RatUp operation-table ledger, and no standard bridge to host number fields is
claimed.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_source\_scope}
\begin{proof}
Unfold \autoref{def:numfield-reflexive-rational-field-extension-carrier}. The
carrier is just the reflexive field-extension carrier of
\autoref{def:fieldext-reflexive-extension-carrier}, so the base and ambient
history predicates, classifiers, and embedding row are the RatUp rows already
used by FieldExtUp.

Use
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage} to account for
the field operations. It says that the base-field operations, ambient-field
operations, vector addition, vector zero, vector negation, and scalar action
are all read from the single RatUp $\FieldUp$ operation table.

Next apply
\autoref{thm:fieldext-reflexive-exact-endpoint-classification} and
\autoref{thm:fieldext-reflexive-ledger-provenance}. These identify every
displayed endpoint with the RatUp classifier class named by the row and record
the ledger provenance inside the RatUp operation table.

Finally use
\autoref{thm:fieldext-reflexive-public-namecert-interface} together with the
RatUp certificate chapter. The public FieldExtUp interface supplies the
visible extension surface, and the RatUp certificate supplies the rational
source rows. Since the NumFieldUp carrier only re-reads these rows and adds no
bridge tuple, the standard bridge field remains absent.
\end{proof}

\begin{theorem}[NumFieldUp reflexive rational finite-extension witness]
\label{thm:numfield-reflexive-rational-finite-extension-witness}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the
finite-extension witness data are the singleton basis data over the reflexive
FieldExtUp vector-space row. The basis list is the one-row unary basis
$[\mathbf{1}_{\mathsf{Rat}}]$, every carried ambient endpoint $m$ has the
coordinate row $m\cdot\mathbf{1}_{\mathsf{Rat}}$, and coordinate equality is
classified by $\mathsf{RatHistoryClassifier}$.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_finite\_extension\_witness}
\begin{proof}
Read the vector-space part of the reflexive FieldExtUp package from
\autoref{def:fieldext-reflexive-extension-carrier}. Its ambient vector carrier
is $\mathsf{RatHistoryCarrier}$, its scalar carrier is the same RatUp carrier,
and its scalar action is RatUp multiplication.

The singleton basis row chooses the RatUp unit endpoint as the only basis
vector. For a carried ambient endpoint $m$, use the scalar $m$ and the basis
vector $\mathbf{1}_{\mathsf{Rat}}$; the multiplication row in the RatUp
$\FieldUp$ table classifies the product with $m$.

Apply
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage} for coverage of
the multiplication and scalar-action rows. Then apply
\autoref{thm:fieldext-reflexive-exact-endpoint-classification} to read the
coordinate endpoint in the same $\mathsf{RatHistoryClassifier}$ class. Thus
the degree witness is the displayed singleton basis over the reflexive
FieldExtUp vector-space row.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_finite\_basis\_witness}

\begin{theorem}[RatUp reflexive NumField coordinate determinacy]
\label{thm:numfield-reflexive-rational-coordinate-determinacy}
For $m,\mathit{coord}:\mathsf{BHist}$, if
$\mathsf{RatHistoryCarrier}(m)$ and $\Cont(m,\emp,\mathit{coord})$, then the
coordinate readback is determined inside the RatUp classifier:
$\mathsf{RatHistoryClassifier}(\mathit{coord},m)$. The same row also forces
$\mathsf{RatHistoryCarrier}(\mathsf{FieldExtSingletonEmbedding}(m))$ and
$\mathsf{RatHistoryClassifier}(\mathsf{FieldExtSingletonEmbedding}(m),m)$.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}. The witness
identifies the displayed coordinate row for a carried endpoint $m$ with
$m\cdot\mathbf{1}_{\mathsf{Rat}}$ over the singleton basis.

The right-unit continuation $\Cont(m,\emp,\mathit{coord})$ reads that product as
the RatUp endpoint named by $m$. Hence the coordinate endpoint remains in the
$\mathsf{RatHistoryClassifier}$ class of $m$.

For the embedded endpoint, use the identity embedding row in
\autoref{def:numfield-reflexive-rational-field-extension-carrier}. It does not
change the $\mathsf{BHist}$ endpoint, so the RatUp carrier predicate and the
same classifier row apply to
$\mathsf{FieldExtSingletonEmbedding}(m)$.
\end{proof}

\begin{theorem}[RatUp reflexive NumField basis row exhaustion]
\label{thm:numfield-reflexive-rational-basis-row-exhaustion}
Every accepted basis display in
\autoref{def:numfield-reflexive-rational-field-extension-carrier} is the
singleton rational unit row $[\mathbf{1}_{\mathsf{Rat}}]$. Every coordinate
readback is classified by
\autoref{thm:numfield-reflexive-rational-coordinate-determinacy}. Thus the
RatUp reflexive $\NumFieldUp$ carrier admits no second basis vector and no
classifier row beyond $\mathsf{RatHistoryClassifier}$.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveSingletonBasisRow\_support\_exactness}
\begin{proof}
First use
\autoref{thm:numfield-reflexive-rational-source-scope}. It fixes the
$\NumFieldUp$ source to the RatUp and FieldExtUp rows and leaves the finite
basis field as the displayed singleton unary basis.

Next apply
\autoref{thm:numfield-reflexive-rational-coordinate-determinacy}. For each
carried coordinate readback, the right-unit row and the identity embedding keep
the coordinate in the RatUp classifier class of the source endpoint.

Finally apply \autoref{thm:numfield-rat-reflexive-ledger-exactness}. Its row
exhaustion says that the FieldExt rows are already exhausted by the RatUp
reflexive certificate and that the NumField contribution is only the singleton
basis row. Therefore neither a second basis vector nor an additional classifier
row is accepted.
\end{proof}

\begin{theorem}[RatUp reflexive NumField degree-one public package]
\label{thm:numfield-reflexive-rational-degree-one-public-package}
The RatUp reflexive carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the source
scope of \autoref{thm:numfield-reflexive-rational-source-scope}, the
finite-extension witness of
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}, the
basis-row exhaustion of
\autoref{thm:numfield-reflexive-rational-basis-row-exhaustion}, and the ledger
exactness of \autoref{thm:numfield-rat-reflexive-ledger-exactness} form the
public degree-one $\NameCert_{\NumFieldUp}$ package. The package exposes carrier
$\mathsf{RatHistoryCarrier}$, classifier $\mathsf{RatHistoryClassifier}$, the
identity embedding, the singleton basis, RatUp scalar action, visible ledger
exactness, and no standard bridge.
\end{theorem}
\begin{proof}
Start with the source certificate
\autoref{thm:rat-history-semantic-name-certificate}. It supplies the concrete
RatUp carrier, classifier, operation table, exact endpoint classification, and
ledger rows consumed by the number-field surface.

Next apply
\autoref{thm:fieldext-reflexive-public-namecert-interface}. This repacks the
same RatUp source as the reflexive FieldExtUp public interface, including the
identity embedding and self-vector-space scalar action.

Use
\autoref{thm:numfield-reflexive-rational-finite-extension-witness} and
\autoref{thm:numfield-reflexive-rational-basis-row-exhaustion} for the
degree-one part. These results identify the only basis display with the
singleton rational unit row and classify every coordinate readback by the RatUp
classifier.

Finally combine
\autoref{thm:numfield-reflexive-rational-source-scope} with
\autoref{thm:numfield-rat-reflexive-ledger-exactness}. The former fixes the
visible $\NumFieldUp$ fields and the absent standard bridge, while the latter
shows that the ledger contains no row beyond the RatUp reflexive FieldExt table
and the singleton basis row. Repacking these fields gives the stated public
degree-one $\NameCert_{\NumFieldUp}$ package.
\end{proof}

\begin{definition}[NumFieldUp RatUp reflexive singleton basis row]
\label{def:numfieldup-rat-reflexive-singleton-basis-row}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the singleton
basis row is the FieldExtUp vector-space singleton row. Its support is the
one-element FieldExt vector carrier entry named by
$\mathsf{FieldSingletonOne}:=\mathsf{BHist.Empty}$.

The RatUp data in the row live only in coordinate readback. For each carried
$m:\mathsf{BHist}$, a coordinate endpoint $coord:\mathsf{BHist}$ is accepted
when $\mathsf{Cont}\ m\ \mathsf{BHist.Empty}\ coord$ holds, and the embedded
ambient endpoint is $\mathsf{FieldExtSingletonEmbedding}\ m$. Thus the basis
support is a FieldExt singleton-vector support, while the coordinate endpoint
and the embedded endpoint are the RatUp-classified rows attached to $m$.
\end{definition}
\leandef{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveSingletonBasisRow}

\begin{theorem}[NumFieldUp RatUp reflexive basis carrier boundary]
\label{thm:numfieldup-rat-reflexive-basis-carried}
In the singleton basis row of
\autoref{def:numfieldup-rat-reflexive-singleton-basis-row}, the basis support is
carried by the FieldExtUp singleton vector carrier. The paper does not assert
$\mathsf{RatHistoryCarrier}\ \mathsf{BHist.Empty}$ for that support. RatUp
carrier hypotheses apply to coordinate endpoints and to embedded ambient
endpoints, not to the bare FieldExt singleton vector marker.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_basis\_support\_boundary}
\begin{proof}
Unfold the singleton basis row of
\autoref{def:numfieldup-rat-reflexive-singleton-basis-row}. The displayed
support entry is
$\mathsf{FieldSingletonOne}:=\mathsf{BHist.Empty}$, so its carrier obligation is
the FieldExt singleton vector carrier obligation.

The RatUp carrier predicate is read on the coordinate side. For a carried
$m:\mathsf{BHist}$, the accepted coordinate row has
$\mathsf{Cont}\ m\ \mathsf{BHist.Empty}\ coord$, and the embedded endpoint is
$\mathsf{FieldExtSingletonEmbedding}\ m$. Apply
$\mathsf{RatHistoryCarrier\_not\_empty}$ to separate this coordinate-side
RatUp carrier from any assertion that $\mathsf{BHist.Empty}$ itself is a RatUp
history carrier endpoint.
\end{proof}

\begin{theorem}[NumFieldUp RatUp reflexive coordinate exactness span]
\label{thm:numfieldup-rat-reflexive-coordinate-exactness}
Let $h,k,c,d:\mathsf{BHist}$. If
$\mathsf{RatHistoryClassifier}\ h\ k$,
$\mathsf{Cont}\ h\ \mathsf{BHist.Empty}\ c$, and
$\mathsf{Cont}\ k\ \mathsf{BHist.Empty}\ d$, then
$\mathsf{RatHistoryClassifier}\ c\ d$ and
$\mathsf{RatHistoryClassifier}\ (\mathsf{FieldExtSingletonEmbedding}\ h)
(\mathsf{FieldExtSingletonEmbedding}\ k)$.
\end{theorem}
\begin{proof}
Apply $\mathsf{cont\_right\_unit\_result}$ to the two coordinate readbacks. This
identifies $c$ with $h$ and $d$ with $k$ in the history classifier class named by
right multiplication with the empty endpoint.

Next use $\mathsf{RatHistoryClassifier\_hsame\_transport}$ to transport the
given classifier $\mathsf{RatHistoryClassifier}\ h\ k$ across these two
right-unit identifications. This yields
$\mathsf{RatHistoryClassifier}\ c\ d$.

For the embedded endpoints, apply
$\mathsf{FieldExtRatReflexive\_exact\_endpoint\_classification}$ to the same
classifier input. The reflexive FieldExt embedding is the singleton embedding
row, so the embedded histories
$\mathsf{FieldExtSingletonEmbedding}\ h$ and
$\mathsf{FieldExtSingletonEmbedding}\ k$ remain in the same RatUp classifier
class.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_coordinate\_exactness\_span}

\begin{theorem}[NumFieldUp reflexive rational coordinate readback uniqueness]
\label{thm:numfield-reflexive-rational-coordinate-readback-uniqueness}
For $m,c_0,c_1:\mathsf{BHist}$, assume
$\mathsf{RatHistoryCarrier}(m)$,
$\mathsf{Cont}(m,\emp,c_0)$, and $\mathsf{Cont}(m,\emp,c_1)$. Then
$\mathsf{RatHistoryClassifier}(c_0,c_1)$, and both
$\mathsf{RatHistoryClassifier}(c_0,m)$ and
$\mathsf{RatHistoryClassifier}(c_1,m)$ hold. Thus the singleton coordinate
row attached to a carried RatUp endpoint is determined by the endpoint itself.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_coordinate\_readback\_pair\_determinacy}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_coordinate\_embedding\_pair\_readback}
\begin{proof}
Apply the continuation right-unit law
\autoref{thm:continuation-right-unit} to $m$. The supplied continuations
$\mathsf{Cont}(m,\emp,c_0)$ and $\mathsf{Cont}(m,\emp,c_1)$ are therefore
right-unit readbacks of the same history, so continuation determinacy
identifies $c_0$ with $m$ and $c_1$ with $m$ up to $\hsame$.

Transport the RatUp carrier row along these two $\hsame$ identifications. The
RatUp semantic name certificate reads endpoint sameness through
$\mathsf{RatHistoryClassifier}$, so the transported rows give
$\mathsf{RatHistoryClassifier}(c_0,m)$ and
$\mathsf{RatHistoryClassifier}(c_1,m)$.

Finally compose the two classifier identifications through $m$. Transitivity
of the RatUp classifier gives $\mathsf{RatHistoryClassifier}(c_0,c_1)$, which
is the required uniqueness of degree-one coordinate readback.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_coordinate\_readback\_uniqueness}

\begin{theorem}[NumFieldUp reflexive rational embedding-coordinate compatibility]
\label{thm:numfield-reflexive-rational-embedding-coordinate-compatibility}
For $m,c_0:\mathsf{BHist}$, assume
$\mathsf{RatHistoryCarrier}(m)$ and $\mathsf{Cont}(m,\emp,c_0)$. Then
$\mathsf{RatHistoryClassifier}(\mathsf{FieldExtSingletonEmbedding}(m),c_0)$.
Equivalently, the identity embedding row consumed from the reflexive
FieldExtUp package is classified with the singleton coordinate row used by the
degree-one NumFieldUp package.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_embedding\_coordinate\_classifier}
\begin{proof}
Use
\autoref{thm:numfield-reflexive-rational-finite-extension-witness} for the
singleton finite-extension surface. It identifies the basis as the one-vector
RatUp basis and reads the coordinate of a carried endpoint through the same
$\mathsf{RatHistoryClassifier}$ row.

Unfold the displayed identity embedding from
\autoref{def:numfield-reflexive-rational-field-extension-carrier}. The
embedding endpoint $\mathsf{FieldExtSingletonEmbedding}(m)$ is the same RatUp
history endpoint $m$ read through the FieldExtUp identity embedding row.

Apply
\autoref{thm:numfield-reflexive-rational-coordinate-readback-uniqueness} to
the carried endpoint $m$, the supplied coordinate $c_0$, and the right-unit
coordinate $m$. The resulting classifier comparison identifies $c_0$ with
$m$, and the identity-embedding display identifies
$\mathsf{FieldExtSingletonEmbedding}(m)$ with the same classifier class.
\end{proof}

\begin{theorem}[NumFieldUp reflexive rational degree-one row exhaustion]
\label{thm:numfield-reflexive-rational-degree-one-row-exhaustion}
Every displayed finite-basis, coordinate, embedding, scalar-action, operation,
exactness, and ledger row admitted by
\autoref{def:numfield-rat-reflexive-carrier} is either one of the exhausted
RatUp reflexive FieldExtUp rows or the singleton degree-one coordinate row.
The singleton row is classified by
\autoref{thm:numfield-reflexive-rational-coordinate-readback-uniqueness} and
is compatible with the identity embedding by
\autoref{thm:numfield-reflexive-rational-embedding-coordinate-compatibility}.
\end{theorem}
\begin{proof}
Unfold \autoref{def:numfield-rat-reflexive-carrier}. The carrier contains the
RatUp reflexive FieldExtUp source pattern together with one finite-basis
field: the singleton basis vector, its coordinate readback, and the
coordinate classifier row.

For the FieldExt part, apply
\autoref{thm:fieldext-ratup-reflexive-certificate-row-exhaustion}. This
exhausts the base-field row, ambient-field row, identity embedding row,
self-vector-space row, scalar-action row, operation-table row, exactness row,
and ledger provenance row by the concrete RatUp $\FieldUp$ table.

It remains to account for the basis field. The basis list has one displayed
entry, the RatUp unit vector, and every coordinate readback is a right-unit
continuation from the carried endpoint. The coordinate uniqueness theorem
classifies any two such readbacks in the same
$\mathsf{RatHistoryClassifier}$ class.

The embedding-coordinate compatibility theorem then identifies the singleton
coordinate row with the identity embedding row. Hence the extra NumFieldUp
surface adds exactly one degree-one coordinate row and no further
finite-basis, embedding, scalar-action, exactness, or ledger row.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_degree\_one\_row\_exhaustion}

\begin{definition}[NumFieldUp reflexive singleton basis coordinate surface]
\label{def:numfield-reflexive-singleton-basis-coordinate-surface}
The reflexive singleton-basis coordinate surface for $\NumFieldUp$ fixes the
concrete BEDC source as RatUp together with the reflexive $\FieldExtUp$ row of
\autoref{def:fieldext-reflexive-extension-carrier}. Its carrier is
$\mathsf{RatHistoryCarrier}$, its classifier is
$\mathsf{RatHistoryClassifier}$, and its finite-basis row is the one-element
row $\mathbf{1}_{\mathsf{Rat}}$.

For each carried ambient endpoint $m:\mathsf{BHist}$, the coordinate readback
is $m$ itself and the reconstruction endpoint is the scalar-action product
$m\cdot\mathbf{1}_{\mathsf{Rat}}$. The ledger is inherited from the RatUp
operation table and the reflexive FieldExtUp row, and the surface is a
paper-proof target without a standard bridge to an external number-field
representation.
\end{definition}

\begin{theorem}[NumFieldUp reflexive singleton basis exhaustion]
\label{thm:numfield-reflexive-singleton-basis-exhaustion}
For the coordinate surface of
\autoref{def:numfield-reflexive-singleton-basis-coordinate-surface}, every
accepted finite-basis row in the carrier is either the unique unit-basis row
$\mathbf{1}_{\mathsf{Rat}}$ or a coordinate row over
$\mathsf{RatHistoryClassifier}$. In particular, no accepted basis,
coordinate, reconstruction, exactness, or ledger row has a coordinate source
outside the RatUp history carrier and classifier.
\end{theorem}
\begin{proof}
Unfold
\autoref{def:numfield-reflexive-singleton-basis-coordinate-surface}. The
surface only exposes the RatUp source, the reflexive FieldExtUp row, and the
one-element basis field $\mathbf{1}_{\mathsf{Rat}}$.

Apply
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}. It
identifies the finite-extension witness with the displayed singleton basis and
reads each coordinate as the carried ambient endpoint $m$ over
$\mathsf{RatHistoryClassifier}$.

For the rows inherited from FieldExtUp, apply
\autoref{thm:fieldext-ratup-reflexive-certificate-row-exhaustion}. This
exhausts the carrier, classifier, embedding, scalar-action, operation,
exactness, and ledger rows by the RatUp reflexive FieldExtUp certificate.

Finally use the RatUp semantic certificate
\autoref{thm:rat-history-semantic-name-certificate}. It makes every accepted
rational endpoint and endpoint comparison a RatUp history-classifier row.
Thus the only remaining finite-basis row is the unit singleton, and every
coordinate readback is classified by $\mathsf{RatHistoryClassifier}$.
\end{proof}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexiveSingletonBasisRow\_coordinate\_transport}

\begin{theorem}[NumFieldUp reflexive embedding coordinate compatibility]
\label{thm:numfield-reflexive-embedding-coordinate-compatibility}
For the coordinate surface of
\autoref{def:numfield-reflexive-singleton-basis-coordinate-surface}, each
carried ambient endpoint $m:\mathsf{BHist}$ has both its identity embedding
coordinate $m$ and its reconstructed endpoint
$m\cdot\mathbf{1}_{\mathsf{Rat}}$ classified by
$\mathsf{RatHistoryClassifier}$. The embedding coordinate and the
reconstruction endpoint therefore live on the same RatUp classifier surface.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldRatReflexive\_embedding\_coordinate\_product\_compatibility}
\begin{proof}
Read the embedding and vector-space rows from the reflexive FieldExtUp public
interface in \autoref{thm:fieldext-reflexive-public-namecert-interface}. In
the reflexive row, the embedding is the identity on
$\mathsf{RatHistoryCarrier}$ and the scalar action is RatUp multiplication.

Use
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage}. The
operation-table coverage includes the multiplication row that interprets the
scalar-action product $m\cdot\mathbf{1}_{\mathsf{Rat}}$ inside the RatUp
operation ledger.

The right-unit row of the RatUp $\FieldUp$ certificate identifies the product
with the original endpoint $m$. Since
\autoref{thm:rat-history-semantic-name-certificate} supplies the RatUp
history classifier for the endpoint $m$, the same classifier also classifies
the reconstructed product endpoint.
\end{proof}

\begin{theorem}[NumFieldUp reflexive degree-one basis exhaustion]
\label{thm:numfield-reflexive-degree-one-basis-exhaustion}
For the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the complete
finite basis surface is the singleton unary row. Its only displayed basis
endpoint is the RatUp unit endpoint $\mathbf{1}_{\mathsf{Rat}}$, every basis
comparison is classified by $\mathsf{RatHistoryClassifier}$, and no
polynomial-root row, primitive-element row, or host-field row belongs to the
basis surface.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_degree\_one\_coordinate\_transport}
\begin{proof}
Unfold
\autoref{def:numfield-reflexive-rational-field-extension-carrier}. The finite
basis field is the basis component of the checked singleton witness in
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}; it has one
displayed endpoint and uses the same RatUp classifier as the ambient endpoint
carrier.

The operation coverage is inherited from
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage}. It accounts
for the RatUp multiplication row used by the scalar action and leaves no
separate operation table for a root, primitive element, or host field.

Finally apply
\autoref{thm:fieldext-ratup-reflexive-certificate-row-exhaustion}. The
FieldExt rows are exhausted by the RatUp base and ambient certificates, the
identity embedding, and the self-vector-space rows. Projecting the remaining
basis component gives exactly the singleton unit row and the
$\mathsf{RatHistoryClassifier}$ comparison row.
\end{proof}

\begin{theorem}[NumFieldUp reflexive coordinate readback determinacy]
\label{thm:numfield-reflexive-coordinate-readback-determinacy}
Let $m:\mathsf{BHist}$ be a carried ambient endpoint in the carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}. If
$c,c':\mathsf{BHist}$ are displayed coordinate histories whose coordinate rows
read back through $\Cont(m,\mathsf{BHist.Empty},c)$ and
$\Cont(m,\mathsf{BHist.Empty},c')$, then $c$ and $c'$ are both
$\mathsf{RatHistoryClassifier}$-equivalent to $m$. Consequently $c$ and $c'$
are $\mathsf{RatHistoryClassifier}$-equivalent to each other.
\end{theorem}
\begin{proof}
Use the singleton finite-extension witness of
\autoref{thm:numfield-reflexive-rational-finite-extension-witness} on the first
displayed coordinate row. The witness reads the coordinate as the scalar $m$
against the unique basis vector $\mathbf{1}_{\mathsf{Rat}}$, so RatUp
multiplication classifies the endpoint $c$ with $m$.

Apply the same witness to the second displayed coordinate row. The same
singleton basis and scalar-action row classify $c'$ with $m$ through
$\mathsf{RatHistoryClassifier}$.

The RatUp classifier laws are the semantic certificate laws supplied by
\autoref{thm:rat-history-semantic-name-certificate}. Symmetry turns the first
classification into the needed direction when necessary, and transitivity
combines the two classifications to obtain the displayed equivalence between
$c$ and $c'$.
\end{proof}

\begin{theorem}[NumFieldUp reflexive finite-extension exactness package]
\label{thm:numfield-reflexive-finite-extension-exactness-package}
The concrete finite-extension part consumed by $\NumFieldUp$ in
\autoref{def:numfield-reflexive-rational-field-extension-carrier} is exhausted
by the identity embedding, the singleton basis of
\autoref{thm:numfield-reflexive-degree-one-basis-exhaustion}, the
coordinate-readback determinacy row of
\autoref{thm:numfield-reflexive-coordinate-readback-determinacy}, the RatUp
scalar-action row, and the RatUp/FieldExt ledger rows. No additional
finite-extension clause is available to downstream $\NumFieldUp$ consumers.
\end{theorem}
\begin{proof}
Start with the concrete carrier consumption statement
\autoref{thm:numfield-reflexive-fieldext-consumption}. It identifies the
underlying FieldExt surface as the RatUp reflexive extension with identity
embedding and self-vector-space scalar action.

The source side is fixed by
\autoref{thm:numfield-reflexive-rational-source-scope}. It says that the
rational carrier, classifier, stability, exactness, and bridge status are read
from the RatUp and FieldExt rows already named there.

For the finite basis field, apply
\autoref{thm:numfield-reflexive-degree-one-basis-exhaustion}. For coordinate
readback, apply
\autoref{thm:numfield-reflexive-coordinate-readback-determinacy}. These two
rows isolate the singleton basis endpoint and the deterministic coordinate
classifier used by every carried ambient endpoint.

Finally combine those rows with
\autoref{thm:numfield-rat-reflexive-ledger-exactness}. The ledger theorem
exhausts the FieldExt rows and the singleton basis row, so repacking with the
identity embedding and RatUp scalar action gives the exact finite-extension
package consumed by $\NumFieldUp$.
\end{proof}
\begin{theorem}[NumFieldUp reflexive rational NameCert obligation package]
\label{thm:numfield-reflexive-rational-namecert-obligation-package}
The carrier of
\autoref{def:numfield-reflexive-rational-field-extension-carrier}, the source
scope of \autoref{thm:numfield-reflexive-rational-source-scope}, and the
finite-extension witness of
\autoref{thm:numfield-reflexive-rational-finite-extension-witness}, together
with the coordinate uniqueness, embedding-coordinate compatibility, and
degree-one row exhaustion of
\autoref{thm:numfield-reflexive-rational-coordinate-readback-uniqueness},
\autoref{thm:numfield-reflexive-rational-embedding-coordinate-compatibility},
and \autoref{thm:numfield-reflexive-rational-degree-one-row-exhaustion},
assemble the paper-side $\NameCert_{\NumFieldUp}$ obligation package. The
package consists of the RatUp rational source, the reflexive FieldExtUp
extension carrier, the identity embedding, the singleton finite basis, the
RatUp classifier exactness row, the RatUp operation-table ledger, and an
absent standard-bridge field.
\end{theorem}
\leanchecked{BEDC.Derived.NumFieldUp.NumFieldReflexiveRational\_namecert\_obligation\_package}
\begin{proof}
Use
\autoref{def:numfield-reflexive-rational-field-extension-carrier} for the
public carrier field. It names the same $\mathsf{BHist}$ carrier and
classifier as RatUp and imports the reflexive FieldExtUp embedding and
vector-space rows.

Use \autoref{thm:numfield-reflexive-rational-source-scope} for source,
classifier, stability, exactness, ledger, and standard-bridge status. Its rows
are precisely the RatUp and FieldExtUp rows cited there.

Use
\autoref{thm:numfield-reflexive-rational-finite-extension-witness} for the
finite-extension field. The singleton basis supplies a concrete degree witness
and the coordinate exactness remains RatUp classifier exactness.

Use
\autoref{thm:numfield-reflexive-rational-coordinate-readback-uniqueness},
\autoref{thm:numfield-reflexive-rational-embedding-coordinate-compatibility},
and \autoref{thm:numfield-reflexive-rational-degree-one-row-exhaustion} for
the reusable degree-one surface. These clauses show that right-unit coordinate
readback is unique, the identity embedding sits in the same RatUp classifier
class as the singleton coordinate, and the displayed rows are exhausted by the
FieldExt table plus that singleton coordinate row.

The public NameCert interface of
\autoref{thm:fieldext-reflexive-public-namecert-interface} packages the
underlying extension surface, while the RatUp certificate chapter supplies the
rational source certificate. Repacking those rows with the singleton basis
gives the displayed paper-side $\NameCert_{\NumFieldUp}$ obligation package
and introduces no parameter-transport schema.
\end{proof}
