\begin{theorem}[Locally convex space sibling dependency route]
\label{thm:locally-convex-space-sibling-dependency-route}
Every $\LocallyConvexSpaceUp$ consumer that exports a locally convex read must first expose the sibling route through the $\TopVecSpaceUp$ topology row, the $\VecSpaceUp$ or module algebra row, the finite seminorm ledger or the optional $\NormUp$ comparison row when present, and the structural $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows. The exported read is therefore a horizontal dependency over the displayed vector, topology, seminorm, norm-comparison, transport, replay, provenance, and naming surfaces; it is not a standalone host predicate for local convexity.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:locally-convex-space-carrier}. Its rows $V,T,S,B,M,H,C,P,N$ already order the vector, topology, seminorm, neighbourhood, comparison, transport, replay, provenance, and naming data.

The sibling route reads $T$ and $V$ before any locally convex probe is exported. The seminorm ledger $S$ supplies finite local convexity probes, and the comparison row $M$ supplies a norm route only when such a row is displayed by the packet.

The structural rows $H,C,P,N$ then transport, replay, source, and name the same finite route. Since no independent host predicate occurs in the carrier, every locally convex read remains tied to the sibling dependency surface.
\end{proof}

\closureat{LocallyConvexSpaceUp}{seedStr}

\begin{closurestatus}{\LocallyConvexSpaceUp}
  \constructivestory{A $\LocallyConvexSpaceUp$ packet is generated from a vector-space source, a topological-vector-space source, a finite seminorm-family ledger, a convex balanced neighbourhood ledger, optional norm comparison rows, componentwise transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:locally-convex-space-carrier}, \autoref{thm:locally-convex-space-namecert-obligations}, \autoref{thm:locally-convex-space-seminorm-filter-stability}, and \autoref{thm:locally-convex-space-sibling-dependency-route} seed the finite locally convex carrier over $V,T,S,B,M,H,C,P,N$ and its sibling dependency route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Hahn--Banach separation, choice-selected duals, ambient weak-star compactness, spectral theory, unrestricted barrelledness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked vector, topological-vector, seminorm, convex balanced neighbourhood, norm comparison, transport, replay, provenance, sibling dependency, and local naming rows for BEDC.Derived.LocallyConvexSpaceUp.}
\end{closurestatus}
