\begin{theorem}[Real unary StreamNameUp finite-window transported selected appended-tail package]
\label{thm:real-unary-streamname-finite-window-transported-selected-appended-tail-package}
For observation maps $s,t,s',t':\Hist\to\Hist$ and histories
$\alpha,\omega,k,u,v,z_s,z_t,d_s,d_t:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega),
$$
and the pointwise transported rows
$$
\forall n:\Hist,\ \mathsf{UnaryHistory}(n)\to\hsame(s(n),s'(n)),
\quad
\forall n:\Hist,\ \mathsf{UnaryHistory}(n)\to\hsame(t(n),t'(n)).
$$
Assume also the displayed transported selected window endpoints
$$
\hsame(s'(\mathsf{append}(\alpha,k)),\Eone(u)),
\quad
\hsame(t'(\mathsf{append}(\alpha,k)),\Eone(v)).
$$
Then the transported selected endpoints carry the selected-shape endpoint
package and the appended e-zero-tail exclusions:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(s'(\mathsf{append}(\alpha,k)),t'(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land\mathsf{UnaryHistory}(v)\land\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s'(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t'(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s'(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t'(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s'(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t'(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s'(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t'(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False})\land\\
(\hsame(s'(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))\to
\mathsf{False})\land\\
(\hsame(t'(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))\to
\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
First derive the selected RatUp classifier at
$\mathsf{append}(\alpha,k)$. Apply
\autoref{thm:real-unary-streamname-finite-window-selected-denominator-package}
to the StreamNameUp classifier, the unary anchor and bound, and the selected
offset. This supplies the untransported selected
$\mathsf{RatHistoryClassifier}$ row, positive denominator rows, unary endpoint
rows, nonempty exclusions, and zero-head exclusions.

The selected index $\mathsf{append}(\alpha,k)$ is unary by the finite-window
offset construction, so the two pointwise rows give
$\hsame(s(\mathsf{append}(\alpha,k)),s'(\mathsf{append}(\alpha,k)))$ and
$\hsame(t(\mathsf{append}(\alpha,k)),t'(\mathsf{append}(\alpha,k)))$.
Transport the selected RatUp classifier across these two comparisons by
\autoref{thm:rat-history-classifier-hsame-transport}. Transport the two
positive denominator rows by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}.

Apply \autoref{thm:rat-history-classifier-e1-tail-unary-iff} to the transported
classifier and the two displayed one-headed endpoint comparisons. This gives
$\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))$, the two unary tail rows,
and $\hsame(u,v)$. Apply
\autoref{thm:positive-unary-denominator-unary-and-nonempty} to the transported
positive-denominator rows; this gives the unary transported endpoint rows and
the two empty endpoint exclusions.

For the zero-head exclusions, suppose first
$\hsame(s'(\mathsf{append}(\alpha,k)),\Ezero(z_s))$. Transport the left
positive-denominator witness across that comparison by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}, contradicting
\autoref{thm:rat-positive-denominator-e0-absurd}. The right zero-head exclusion
is the same argument using $t'(\mathsf{append}(\alpha,k))$ and $\Ezero(z_t)$.

It remains to rule out the appended e-zero tails. For the left endpoint,
suppose
$\hsame(s'(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))$. Transport the
positive denominator witness for $s'(\mathsf{append}(\alpha,k))$ across this
comparison by \autoref{thm:rat-positive-unary-denominator-hsame-transport}.
The transported witness contradicts
\autoref{thm:positive-unary-denominator-append-e0-tail-absurd}.

The right endpoint is identical. A display
$\hsame(t'(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))$ transports the
positive denominator witness for $t'(\mathsf{append}(\alpha,k))$ to
$d_t\cdot\Ezero(z_t)$, and the same appended e-zero-tail obstruction
contradicts that transported witness.

Repack the transported classifier, displayed e-one readback rows, denominator
rows, endpoint exclusions, and appended-tail contradictions. These rows are
exactly the transported selected endpoint package.
\end{proof}

Fit. Traditional target: transported finite-window rational readback with
appended-tail endpoint obstruction for RealUp StreamNameUp classifiers. BEDC
source: $\StreamNameUp+\RealUp+\RatUp$ over $\mathsf{BHist}$. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ transported to the selected
$\mathsf{RatHistoryClassifier}$. Stability: pointwise $\hsame$ transport of
StreamNameUp endpoints and positive-denominator transport to appended tails.
Ledger: carrier, classifier, unary anchor, unary bound, selected offset,
pointwise transport rows, one-headed endpoint displays, zero-head tests, and
appended-tail displays. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-transported-selected-appended-tail-package}.
Exactness: transported selected endpoint package plus the two appended
e-zero-tail exclusion rows. Standard bridge: finite rational observation
windows. Status: $\mathsf{ProofTarget}$.
