\chapter{A Concrete Naming Certificate for $\CauchyProductUp$}
\label{ch:concrete-instances-cauchyproduct-namecert}
\origin{human}

The $\CauchyProductUp$ interface names the finite product certificate for two regular Cauchy names. It expresses the Bishop--Bridges constructive product of regular Cauchy sequences as displayed $\NameCert$ rows over scheduled finite windows, dyadic observations, regular rational readback, and the $\RealUp$ seal, without adding quotient streams or an ambient completeness operation.

\begin{definition}[CauchyProduct NameCert source]
\label{def:cauchy-product-namecert-source}
A $\CauchyProductUp$ source is a finite $\mathsf{BHist}$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $X$ and $Y$ are the two $\RegularCauchyNameUp$ source rows;
\item $W_X$ and $W_Y$ are the paired $\StreamNameUp$ finite-window schedules for a shared precision request;
\item $M_X$ and $M_Y$ are the paired dyadic-radius rows bounding the two source windows;
\item $Q_X$ and $Q_Y$ are the $\DyadicRatCoreUp$ observation rows read from the scheduled windows;
\item $P$ is the pointwise product observation row formed from $Q_X$ and $Q_Y$ inside the displayed dyadic rational core;
\item $E$ is the $\RegSeqRatUp$ classifier row for the product observation and its finite radius ledger;
\item $H$ stores the displayed $\hsame$ transports for the two source names, both stream windows, both radius rows, both dyadic observations, the product observation, and the regular rational readback;
\item $C$ stores the displayed $\Cont$ routes for reading the source windows, transporting the dyadic product observation, exposing the regular rational classifier, and handing the result to the real seal;
\item $L$ is the finite ledger recording the paired input radii, the product-radius row, the $\RealUp$ seal handoff, and the $\Pkg$ provenance over $\RegularCauchyNameUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CauchyProductUp}$ row.
\end{enumerate}
The packet stores a finite product construction. It contains no quotient stream, host multiplication primitive, selected limit, trichotomy row, independent real carrier, or ambient completeness coordinate.
\end{definition}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyProduct NameCert obligations]
\label{thm:cauchy-product-namecert-obligations}
The local $\NameCert_{\CauchyProductUp}$ surface for the source packet of \autoref{def:cauchy-product-namecert-source} consists exactly of carrier admission, paired $\RegularCauchyNameUp$ source admission, paired $\StreamNameUp$ window scheduling, dyadic-radius routing, $\DyadicRatCoreUp$ product observation, pointwise $\RegSeqRatUp$ classifier exposure, $\RealUp$ seal handoff, displayed $\hsame$ and $\Cont$ transport, package provenance, finite ledger, and the local naming row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from the displayed packet $Z$. Its coordinates list the two regular Cauchy sources, their paired stream windows, the radius rows, dyadic observations, product observation, readback classifier, transport rows, continuation routes, ledger, and local certificate.

The analytic product step is finite. The two window reads expose $Q_X$ and $Q_Y$ inside $\DyadicRatCoreUp$, and the product observation row $P$ is the only row that combines them. The classifier row $E$ then reads this product observation with the radius information stored in the ledger.

The remaining obligations are provenance obligations. The rows $H,C,L,N$ carry transport, continuation, package, seal handoff, and local naming data, so the certificate has no source from which to read host multiplication, quotient equality, selected limits, trichotomy, or completeness.
\end{proof}

\begin{theorem}[CauchyProduct root window obligations]
\label{thm:cauchy-product-root-window-obligations}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the root-facing paired-window obligation is anchored in the $\BHist$ rows $X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y$. The two $\RegularCauchyNameUp$ sources may be consumed only through the paired $\StreamNameUp$ schedules and the shared finite tail threshold surface used by \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}; no consumer may replace those windows by quotient streams, selected limits, host multiplication, or an ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_window\_obligations}
\begin{proof}
Begin with the carrier and NameCert obligations. \autoref{def:cauchy-product-namecert-source} displays the two source rows and paired window rows, while \autoref{thm:cauchy-product-namecert-obligations} makes those rows part of the local certificate surface.

Use the StreamName handoff of \autoref{thm:cauchy-product-streamname-handoff}. It forces every product read to pass through $W_X,W_Y$ before $Q_X,Q_Y$, $M_X,M_Y$, $P$, and $E$ can be inspected.

Finally read the shared-tail consumer through \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. The tail-meet packet consumes the same kind of finite threshold window, so the CauchyProduct root obligation is a paired finite-window row rather than a quotient or completed-real operation.
\end{proof}

\begin{theorem}[CauchyProduct root budget obligations]
\label{thm:cauchy-product-root-budget-obligations}
The product-radius budget obligation of an accepted $\CauchyProductUp$ packet is a finite $\BHist$ route from the paired radius rows $M_X,M_Y$ and dyadic rows $Q_X,Q_Y$ through the product observation $P$ to the classifier row $E$ and ledger row $L$. It is routed only by the displayed $\hsame$ transports, $\Cont$ continuations, $\Pkg$ provenance, and local $\NameCert_{\CauchyProductUp}$ row, and it exposes no radius oracle, host multiplication estimate, quotient stream, selected limit, trichotomy row, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with the source packet. The only budget-relevant coordinates are $M_X,M_Y,Q_X,Q_Y,P,E,L$ together with the structural rows $H,C,N$.

Apply \autoref{thm:cauchy-product-namecert-obligations} and \autoref{thm:cauchy-product-streamname-handoff}. These make the dyadic and radius rows visible only after the paired finite windows, and they route the product observation through the same local certificate.

The budget route is then exact by \autoref{thm:cauchy-product-radius-ledger-exactness}. Since that theorem binds the product-radius ledger to the displayed path into $E$, no unrecorded radius oracle or analytic primitive can enter the root obligation.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_budget\_obligations}

\begin{theorem}[CauchyProduct root Real seal obligations]
\label{thm:cauchy-product-root-real-seal-obligations}
Every root-facing $\RealUp$ seal read of an accepted $\CauchyProductUp$ packet factors through the finite rows
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and through the shared tail-threshold consumption surface of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. The seal read cannot escape to host multiplication, RealUp completeness, quotient-stream equality, selected limits, trichotomy, independent real carriers, or an ambient completeness operation.
\end{theorem}
\begin{proof}
First combine the root window obligations with the root budget obligations. The former fixes the paired finite windows, and the latter fixes the product-radius route from those windows through the dyadic observations to the classifier and ledger.

Next apply \autoref{thm:cauchy-product-real-seal-boundary}. The $\RealUp$ seal reads the product only through the $\RegSeqRatUp$ classifier row $E$ together with the displayed ledger, transport, continuation, provenance, and local naming rows.

Finally use \autoref{thm:cauchy-product-real-seal-consumer-exhaustion}. It exhausts every real-facing consumer route by the same finite inventory, while the sibling tail-meet packet supplies only the shared finite threshold surface. Hence the root seal obligation is finite-row based and has no escape to the excluded analytic objects.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_real\_seal\_obligations}

\begin{theorem}[CauchyProduct root window seal compatibility]
\label{thm:cauchy-product-root-window-seal-compatibility}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the paired $\StreamNameUp$ windows $W_X,W_Y$ and the product-radius budget recorded through $M_X,M_Y,Q_X,Q_Y,P,L$ are the only route through which a $\RealUp$ seal consumer reaches the classifier row $E$. The route is the one named by the root window obligations, root budget obligations, and root Real seal obligations; it admits no host multiplication, quotient stream, selected limit, trichotomy row, or ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-product-root-window-obligations}. It places every root-facing product read downstream of the paired finite windows $W_X,W_Y$.

Apply \autoref{thm:cauchy-product-root-budget-obligations}. The product-radius route is then fixed through $M_X,M_Y,Q_X,Q_Y,P,L$ before the classifier row can be inspected.

Finally use \autoref{thm:cauchy-product-root-real-seal-obligations}. The $\RealUp$ seal reads $E$ only after the paired windows and budget route have been consumed, so none of the excluded analytic objects has a coordinate in the accepted packet.
\end{proof}

\begin{theorem}[CauchyProduct root obligation package]
\label{thm:cauchy-product-root-obligation-package}
Every accepted $\CauchyProductUp$ packet supplies a root-unblock package consisting of carrier admission, paired-window source rows, product-budget exactness, Real seal compatibility, $\hsame$ and $\Cont$ transport, $\Pkg$ provenance, and the local $\NameCert_{\CauchyProductUp}$ rows. The package is the finite surface
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N,
$$
and it excludes host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, and ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_obligation\_package}
\begin{proof}
First read carrier admission and NameCert obligations through \autoref{def:cauchy-product-namecert-source} and \autoref{thm:cauchy-product-namecert-obligations}. These give the two source names, paired windows, dyadic rows, product observation, classifier row, transport rows, continuation routes, ledger, provenance, and local naming row.

Next assemble the root route. The root window obligations provide the paired-window source surface, the root budget obligations provide the product-radius accounting, and \autoref{thm:cauchy-product-root-window-seal-compatibility} identifies the Real seal route through the same rows.

Finally apply the root Real seal obligations. They keep the seal consumer inside the displayed packet and preserve the exclusions on host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, and ambient completeness. The listed rows therefore form the root-unblock package.
\end{proof}

\begin{theorem}[CauchyProduct root source-pair lock]
\label{thm:cauchy-product-root-source-pair-lock}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the two $\RegularCauchyNameUp$ source rows $X,Y$ and their paired $\StreamNameUp$ window rows $W_X,W_Y$ are locked before any product observation row is read. A consumer cannot inspect $P$ until the carrier admission, local $\NameCert_{\CauchyProductUp}$ obligations, and the $\StreamNameUp$ handoff have exposed the two source rows as one paired finite-window route.
\end{theorem}
\begin{proof}
Read the carrier from \autoref{def:cauchy-product-namecert-source}. The first four rows of $Z$ are the two regular Cauchy sources and their paired stream windows, before the radius, dyadic observation, product, classifier, and seal-facing rows.

Apply \autoref{thm:cauchy-product-namecert-obligations}. It makes paired source admission and paired window scheduling part of the local certificate surface rather than optional consumer data.

Finally use \autoref{thm:cauchy-product-streamname-handoff}. It routes every product read through $W_X,W_Y$ before exposing $Q_X,Q_Y$, $M_X,M_Y$, $P$, or $E$, so the accepted packet locks the two source rows before any product observation is available.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_window\_read\_stability}

\begin{theorem}[CauchyProduct root product observation route]
\label{thm:cauchy-product-root-product-observation-route}
For an accepted $\CauchyProductUp$ packet, the product observation row $P$ is reachable only along the finite route
$$
X,Y \longmapsto W_X,W_Y \longmapsto Q_X,Q_Y \longmapsto M_X,M_Y \longmapsto P.
$$
The route reads paired $\StreamNameUp$ windows, dyadic observation rows, and radius rows, and it exposes no host multiplication primitive, quotient stream, selected limit, independent real carrier, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start from the source-pair lock in \autoref{thm:cauchy-product-root-source-pair-lock}. The consumer has already passed through the two source rows and their paired stream windows before any product-facing row is visible.

Use \autoref{thm:cauchy-product-streamname-handoff}. The handoff exposes $Q_X,Q_Y$ and $M_X,M_Y$ from the paired schedules before the product row $P$ is formed.

Now apply \autoref{thm:cauchy-product-root-budget-obligations}. The product-radius budget keeps $P$ inside the same finite $\BHist$ route and rules out any extra radius oracle or analytic multiplication coordinate.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_product\_observation\_route}

\begin{theorem}[CauchyProduct root downstream unblock surface]
\label{thm:cauchy-product-root-downstream-unblock-surface}
The root-unblock surface of an accepted $\CauchyProductUp$ packet is the finite union of the source-pair lock, the product-observation route, the root budget obligations, the root $\RealUp$ seal obligations, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\CauchyProductUp}$ rows. Downstream $\RealUp$ and $\RegSeqRatUp$ product consumers read only this union and cannot import quotient streams, host multiplication, selected limits, trichotomy, independent real carriers, or ambient completeness.
\end{theorem}
\begin{proof}
First combine \autoref{thm:cauchy-product-root-source-pair-lock} and \autoref{thm:cauchy-product-root-product-observation-route}. These identify the source-window side and the finite product-observation path into $P$.

Next apply \autoref{thm:cauchy-product-root-budget-obligations}. The same route is extended through the product-radius ledger toward $E$ and $L$, with no extra analytic coordinate.

Finally use \autoref{thm:cauchy-product-root-real-seal-obligations} together with \autoref{thm:cauchy-product-namecert-obligations}. The seal, transport, continuation, provenance, and local naming rows are already part of the displayed packet, so the downstream unblock surface is exactly the stated finite union.
\end{proof}

\begin{theorem}[CauchyProduct paired-window source admission]
\label{thm:cauchy-product-paired-window-source-admission}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the rows $X,Y,W_X,W_Y$ are admitted only as paired $\StreamNameUp$ finite-window source rows over the two $\RegularCauchyNameUp$ inputs. The admission route is the one exposed by the sibling surfaces \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}; it has no quotient-stream, selected-limit, host multiplication, or ambient-completeness coordinate.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-product-root-obligation-package}. It identifies $X,Y,W_X,W_Y$ as the source side of the root package for the product packet.

Apply \autoref{thm:cauchy-product-root-window-obligations}. The two source names can be consumed only through the paired finite windows $W_X,W_Y$, and the route is downstream of the displayed $\StreamNameUp$ schedule rows.

The sibling StreamName and RegSeqRat surfaces provide the dependency anchors for the window and source-name reads. Because the root package excludes quotient streams, selected limits, host multiplication, and ambient completeness, no other source-admission route is available.
\end{proof}

\begin{theorem}[CauchyProduct budget route exactness]
\label{thm:cauchy-product-budget-route-exactness}
For an accepted $\CauchyProductUp$ packet, the rows
$$
M_X,M_Y,Q_X,Q_Y,P,L
$$
are the exact finite budget route into the $\RegSeqRatUp$ classifier row $E$. The route reads dyadic observations through \autoref{ch:concrete-instances-dyadicratcore-namecert}, records its regular-rational classifier through \autoref{ch:concrete-instances-regseqrat-namecert}, and admits no radius oracle, quotient stream, selected limit, host multiplication estimate, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:cauchy-product-root-budget-obligations}. It lists $M_X,M_Y,Q_X,Q_Y,P,E,L$ as the finite product-radius route.

Use \autoref{thm:cauchy-product-root-obligation-package} to keep the same route inside the carrier, transport, continuation, provenance, and local naming rows. The dyadic observation surface comes from the displayed $Q_X,Q_Y$ rows, and the product observation $P$ is the only combining row.

Finally apply \autoref{thm:cauchy-product-root-window-seal-compatibility}. The classifier row $E$ is reached only after the budget ledger $L$ has consumed those rows, so the sibling DyadicRatCore and RegSeqRat surfaces are the whole classifier-facing budget path.
\end{proof}

\begin{theorem}[CauchyProduct paired-window ledger classifier]
\label{thm:cauchy-product-paired-window-ledger-classifier}
The paired window rows $W_X,W_Y$ together with the ledger route $M_X,M_Y,Q_X,Q_Y,P,L$ determine the classifier-facing product row $E$ consumed by the $\RealUp$ seal. This determination is routed through the sibling surfaces \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}, and it exposes no independent real carrier, selected limit, quotient stream, trichotomy row, host multiplication primitive, or ambient completeness operation.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_paired\_window\_ledger\_classifier}
\begin{proof}
First combine \autoref{thm:cauchy-product-paired-window-source-admission} with \autoref{thm:cauchy-product-budget-route-exactness}. The paired windows provide the source reads, and the budget route provides the dyadic product observation and ledger feeding $E$.

Next use \autoref{thm:cauchy-product-root-real-seal-obligations}. The $\RealUp$ seal consumes the product only after the classifier row $E$ has been reached through the same finite windows, dyadic observations, product row, ledger, transport, continuation, provenance, and local naming rows.

The sibling surfaces account for each dependency edge: StreamName for finite windows, DyadicRatCore for observations and product rows, RegSeqRat for the classifier readback, and RealUp for the seal. Therefore the classifier-facing product row is determined by the paired-window ledger route and by no excluded analytic object.
\end{proof}

\begin{theorem}[CauchyProduct root window seal stability]
\label{thm:cauchy-product-root-window-seal-stability}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the paired window rows $W_X,W_Y$ remain the unique route to every seal-facing product row under componentwise $\hsame$ transport and displayed $\Cont$ replay. A seal consumer reaches $P$, $E$, and the ledger row $L$ only through the route fixed by the paired $\StreamNameUp$ windows, the dyadic observations, the product-radius ledger, package provenance, and local $\NameCert_{\CauchyProductUp}$ row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_window\_seal\_stability}
\begin{proof}
Start with the root window obligations. They force every root-facing product read through the paired finite windows $W_X,W_Y$ before the dyadic rows, radius rows, product row, classifier row, or seal-facing ledger can be inspected.

Now apply the StreamName handoff and window product stability. The handoff fixes the route from $W_X,W_Y$ to $Q_X,Q_Y,M_X,M_Y,P,E$, while stability keeps that route invariant under the componentwise transport row $H$ and the continuation replay row $C$.

Finally use the root Real seal obligations. Since the $\RealUp$ seal can read the product only after the same window and ledger route has been consumed, no second path to a seal-facing row is available inside the accepted packet.
\end{proof}

\begin{theorem}[CauchyProduct root RegSeqRat seal stability]
\label{thm:cauchy-product-root-regseq-seal-stability}
For an accepted $\CauchyProductUp$ packet
$$
Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N),
$$
the product observation row $P$ and the product-radius ledger row $L$ determine the $\RegSeqRatUp$ classifier row $E$ before any $\RealUp$ seal read is available. The determining route is the finite path through the paired windows, dyadic observations, radius rows, displayed $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local NameCert row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_regseq\_seal\_stability}
\begin{proof}
First apply the root budget obligations. They bind $M_X,M_Y,Q_X,Q_Y,P,E,L$ as the finite product-radius route downstream of the paired windows.

Use radius ledger exactness to identify $L$ with the displayed route from the input-radius rows and dyadic observations through the product observation $P$. Then apply radius product regularity to recover the classifier row $E$ from exactly that ledgered product route.

The root Real seal obligations place every real-facing read after this classifier. Hence the $\RegSeqRatUp$ row is determined before the seal is consumed, and the seal cannot supply an independent classifier, quotient stream, selected limit, trichotomy row, host multiplication row, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[CauchyProduct root RealObservationBudget seal boundary]
\label{thm:cauchy-product-root-real-budget-seal-boundary}
Every $\RealObservationBudgetUp$ consumer of an accepted $\CauchyProductUp$ packet reads the product only through the union of the CauchyProduct rows
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and the budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
The boundary exposes no quotient stream, selected limit, trichotomy row, host multiplication primitive, independent real carrier, ambient completeness coordinate, or additional real-facing product route.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_real\_budget\_seal\_boundary}
\begin{proof}
Begin with root window seal stability and root RegSeqRat seal stability. These place the product route through the paired windows, the product observation, the radius ledger, and the classifier row before any real-facing budget consumer can read the seal.

Now compose with the Real observation budget handoff. It routes the product seal through the accepted budget packet before the consumer reaches its real-facing rows.

Use the observation budget RegSeq handoff to identify the classifier read with the budgeted regular-sequence row. Finally apply the budgeted product consumer boundary; it exhausts the joined interface by the displayed product rows and budget rows, leaving no coordinate for any excluded analytic object.
\end{proof}

\begin{theorem}[CauchyProduct StreamName handoff]
\label{thm:cauchy-product-streamname-handoff}
Every accepted $\CauchyProductUp$ packet routes a product read through the paired $\StreamNameUp$ windows $W_X,W_Y$ before exposing the $\DyadicRatCoreUp$ observations $Q_X,Q_Y$, the dyadic-radius rows $M_X,M_Y$, the product observation $P$, and the pointwise $\RegSeqRatUp$ classifier row $E$. No consumer can read a product row without first reading those finite schedules and their displayed provenance.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_streamname\_handoff}
\begin{proof}
Start with the two source rows $X$ and $Y$. Each is read only through its displayed $\RegularCauchyNameUp$ source row and the matching finite $\StreamNameUp$ schedule.

The dyadic product row is downstream of the schedules. Once $W_X$ and $W_Y$ have exposed $Q_X,Q_Y$ and $M_X,M_Y$, the row $P$ records the finite dyadic product observation and $E$ repacks it as a pointwise regular rational classifier.

The transport and continuation rows preserve this order. Since $H,C,L,N$ are attached to the same paired windows, a consumer has no alternate route to a host sequence, quotient product, selected limit, or ambient real operation.
\end{proof}

\begin{theorem}[CauchyProduct Real seal boundary]
\label{thm:cauchy-product-real-seal-boundary}
Any $\RealUp$ consumer of an accepted $\CauchyProductUp$ packet reads only the $\RegSeqRatUp$ classifier row $E$ built from the paired $\StreamNameUp$ windows, dyadic-radius rows, $\DyadicRatCoreUp$ product observation, displayed $\hsame$ transports, $\Cont$ routes, finite ledger, package provenance, and local $\NameCert_{\CauchyProductUp}$ row. The seal boundary exports no RealUp completeness theorem, quotient stream, selected limit, trichotomy row, independent real carrier, or host multiplication primitive.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_boundary}
\begin{proof}
Factor the real-facing read through the pointwise regular classifier. By \autoref{thm:cauchy-product-streamname-handoff}, the classifier is already downstream of the two finite stream windows and their dyadic product observation.

The real seal is recorded in the ledger row rather than supplied by an ambient carrier. Thus a $\RealUp$ consumer receives $E$ together with $H,C,L,N$, which are exactly the displayed transport, continuation, ledger, package, and naming rows.

No other coordinate in \autoref{def:cauchy-product-namecert-source} can supply completeness, quotient equality, a selected limit, trichotomy, or host multiplication. The real-facing boundary is therefore exhausted by the finite product packet.
\end{proof}

\begin{theorem}[CauchyProduct public interface export]
\label{thm:cauchy-product-public-interface-export}
Every public consumer of an accepted $\CauchyProductUp$ packet reads the product through the paired-window source rows, the finite budget route, the ledger classifier, the $\StreamNameUp$ handoff, and the $\RealUp$ seal boundary. Equivalently, the public export surface is the finite route through $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$ together with the displayed source, budget, provenance, continuation, and naming rows; it exports no quotient stream equality, selected infinite sum, host multiplication primitive, trichotomy row, independent real carrier, or ambient completeness claim.
\end{theorem}
\begin{proof}
First use the paired-window source surface. The StreamName handoff, \autoref{thm:cauchy-product-streamname-handoff}, places every product read behind the two finite windows $W_X,W_Y$ and the dyadic observation rows $Q_X,Q_Y,M_X,M_Y$.

Next compose the budget route with the classifier route. The root RealObservationBudget seal boundary identifies the budget-facing rows, while the root RegSeqRat seal stability theorem makes the classifier row $E$ downstream of the product observation and ledger.

Finally apply the Real seal boundary, \autoref{thm:cauchy-product-real-seal-boundary}. It exhausts the public read through the displayed finite rows and excludes quotient streams, selected limits, trichotomy, host multiplication, independent real carriers, and ambient completeness. This is exactly the stated export surface.
\end{proof}

\begin{theorem}[CauchyProduct RealSeries consumer boundary]
\label{thm:cauchy-product-real-series-consumer-boundary}
Every $\RealSeriesUp$ consumer of an accepted $\CauchyProductUp$ packet factors through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RealAlgOrderUp$, $\RealSeriesUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The consumer may read the product only through the public interface of \autoref{thm:cauchy-product-public-interface-export}; it receives no selected infinite sum, quotient stream equality, host multiplication primitive, order trichotomy, independent real carrier, or ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with a RealSeries-facing read. The public interface export theorem routes the read through the paired finite windows, dyadic ledgers, product observation, classifier, transports, continuations, provenance, and local name.

The series consumer can then inspect only the named BEDC rows. Its stream access is through $\StreamNameUp$, its rational readback is through $\RegSeqRatUp$, its real-facing seal is through $\RealUp$, and its order-facing comparison surface is through $\RealAlgOrderUp$ before the $\RealSeriesUp$ row is consumed.

The structural rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ preserve that route without adding analytic data. Applying \autoref{thm:cauchy-product-real-seal-boundary} removes any remaining path to a selected infinite sum, quotient stream equality, host multiplication primitive, order trichotomy, independent real carrier, or ambient completeness witness.
\end{proof}

\begin{theorem}[CauchyProduct public RealSeries export]
\label{thm:cauchy-product-public-real-series-export}
Every public $\RealSeriesUp$-facing export of an accepted $\CauchyProductUp$ packet is the composition of paired-window source admission, budget route exactness, paired-window ledger classification, public interface export, and the RealSeries consumer boundary. The exported surface is exactly the finite route through
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the $\RealSeriesUp$ row. It supplies no quotient stream, selected infinite sum, host multiplication, order trichotomy, independent real carrier, or ambient completeness.
\end{theorem}
\begin{proof}
Start with paired-window source admission and budget route exactness. The source rows $X,Y,W_X,W_Y$ and the budget rows $M_X,M_Y,Q_X,Q_Y,P,L$ are fixed by \autoref{thm:cauchy-product-paired-window-source-admission} and \autoref{thm:cauchy-product-budget-route-exactness}.

Next apply the paired-window ledger classifier. \autoref{thm:cauchy-product-paired-window-ledger-classifier} places the classifier row $E$ downstream of those windows, dyadic observations, product row, and ledger.

Now use the public interface export. \autoref{thm:cauchy-product-public-interface-export} packages the same finite route with the displayed transport, continuation, provenance, and local naming rows $H,C,N$.

Finally apply the RealSeries consumer boundary. It attaches the $\RealSeriesUp$ consumer row only after the public CauchyProduct surface has been read, and it rules out the excluded quotient, sum-selection, host-multiplication, trichotomy, independent-carrier, and completeness objects.
\end{proof}

\input{parts/concrete_instances/cauchyproduct/formal_marker_sync_and_product_tail}
