\begin{theorem}[CauchyProduct Real seal upstream dependency]
\label{thm:cauchy-product-real-seal-upstream-dependency}
Every accepted $\CauchyProductUp$ Real-seal read consumed by a completion-facing downstream chapter first consumes the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the product budget ledger, the $\RegSeqRatUp$ classifier row, and the $\RealUp$ seal surface. In displayed coordinates, the upstream route is the finite packet
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with any accepted observation-budget rows when the consumer uses a budget packet. The route exports no quotient stream, selected product limit, host multiplication primitive, trichotomy row, independent real carrier, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_upstream\_dependency}
\begin{proof}
Start with paired-window source admission from \autoref{thm:cauchy-product-root-source-window-totality} and \autoref{thm:cauchy-product-root-source-admission}. These rows force the two source names $X,Y$ to enter the product packet through the paired $\StreamNameUp$ windows $W_X,W_Y$.

Next use budget route exactness from \autoref{thm:cauchy-product-root-budget-product-lock} and \autoref{thm:cauchy-product-radius-budget-conservation}. The dyadic observations $Q_X,Q_Y$, source-radius rows $M_X,M_Y$, product row $P$, and ledger row $L$ form the budget route before the classifier can be read.

Apply the paired-window ledger classifier results \autoref{thm:cauchy-product-root-shared-window-product-classifier} and \autoref{thm:cauchy-product-real-classifier-obligation}. They identify the $\RegSeqRatUp$ row $E$ as downstream of the same finite windows, dyadic observations, and product ledger.

Finally use the root Real seal obligations and consumer exhaustion supplied by \autoref{thm:cauchy-product-root-real-seal-product-ledger}, \autoref{thm:cauchy-product-real-completion-consumer-lock}, and \autoref{thm:cauchy-product-root-phase-handoff}. The completion-facing consumer therefore reaches the $\RealUp$ seal only through the displayed upstream route and cannot import any excluded analytic object.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName CauchyProduct handoff]
\label{thm:real-regseqrat-streamname-cauchyproduct-handoff}
An accepted $\CauchyProductUp$ route consumed by a Real-completion-facing chapter is equivalent, as a finite BEDC handoff surface, to the ordered visibility chain consisting of paired $\StreamNameUp$ windows, dyadic observations, the product budget ledger, the $\RegSeqRatUp$ classifier row, and the $\RealUp$ seal. In coordinates, the handoff surface is exhausted by
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the accepted observation-budget rows when a budget consumer asks for them. It exports no quotient stream, host multiplication primitive, trichotomy row, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_regseqrat\_streamname\_handoff}
\begin{proof}
First read the ordered source surface. The paired-window totality of \autoref{thm:cauchy-product-root-source-window-totality} forces the two source names $X,Y$ to be visible only through the paired $\StreamNameUp$ windows $W_X,W_Y$ before any product consumer can inspect the downstream rows.

Next read the budget and classifier surface. The budget product lock of \autoref{thm:cauchy-product-root-budget-product-lock} places the dyadic observations, source-radius rows, product row, and ledger row before the classifier, and \autoref{thm:cauchy-product-real-classifier-obligation} identifies the resulting $E$ row as the finite $\RegSeqRatUp$ classifier consumed by the Real route.

Finally apply the upstream dependency theorem \autoref{thm:cauchy-product-real-seal-upstream-dependency}. It states that a completion-facing Real-seal read reaches the $\RealUp$ seal only through exactly those prior rows, so the ordered chain is both sufficient for the handoff and exhaustive for accepted consumers. Coordinate exhaustion gives the exclusions: no quotient stream, host multiplication, trichotomy, or ambient completeness coordinate is present.
\end{proof}

\begin{theorem}[CauchyProduct LimitSeal sibling dependency]
\label{thm:cauchy-product-limitseal-sibling-dependency}
Every accepted $\CauchyProductUp$ Real-seal route that reaches the $\RealUp$ seal passes through the same finite rows consumed by the $\CauchyLimitSealUp$ compatibility boundary of \autoref{ch:concrete-instances-cauchylimitseal-namecert}: paired $\StreamNameUp$ windows, dyadic observations, the product budget ledger, the $\RegSeqRatUp$ classifier, transport rows, route rows, package provenance, and local $\NameCert$ rows. The sibling dependency supplies a horizontal handoff edge only; it imports no selected product limit, quotient stream, host multiplication primitive, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_limitseal\_sibling\_dependency}
\begin{proof}
Begin with the upstream dependency theorem. It places every completion-facing Real-seal read of a $\CauchyProductUp$ packet on the paired windows, dyadic observations, product budget ledger, classifier row, and displayed structural rows before the $\RealUp$ seal is consumed.

Next use the Real--RegSeqRat--StreamName handoff. That handoff identifies the same finite ordered surface as the route seen by a downstream Real-completion consumer.

Read this finite surface against the $\CauchyLimitSealUp$ compatibility boundary named in \autoref{ch:concrete-instances-cauchylimitseal-namecert}. That boundary consumes $\StreamNameUp$, $\RegSeqRatUp$, dyadic observation, $\RealUp$, transport, route, package, and local naming rows, so the product route and the limit-seal route meet on those rows.

The conclusion is only a sibling dependency. Since neither cited product theorem exports a quotient stream, selected product limit, host multiplication primitive, or ambient completeness row, the horizontal edge adds no analytic coordinate beyond the displayed finite BEDC surface.
\end{proof}

\begin{theorem}[CauchyProduct shared-selector Real seal stability]
\label{thm:cauchy-product-shared-selector-real-seal-associativity}
Let two accepted $\CauchyProductUp$ packets read their factor windows through
the same $\FiniteObservationBudgetSelectorUp$ route. Suppose the displayed
$\StreamNameUp$ windows, dyadic radius rows, $\RegSeqRatUp$ classifier row, and
$\RealUp$ seal boundary agree componentwise on the public packet rows. Then
every multiplication-facing $\RealUp$ seal consumer of the two packets reads
the same finite product-route surface
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the shared selector rows. The shared selector can be reused
without changing the product seal surface, and the route exports no host
multiplication, quotient-stream product, selected limit, trichotomy row, or
ambient completeness datum.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_shared\_selector\_real\_seal\_stability}
\begin{proof}
First apply the budget-selector distributive lock
\autoref{thm:cauchy-product-budget-selector-distributive-lock}. It identifies
both factor-window reads with one finite selector route and one displayed
product-route certificate.

Next use the Real budget multiplication boundary
\autoref{thm:cauchy-product-real-budget-multiplication-boundary}. A
multiplication-facing $\RealUp$ seal read is available only after the shared
windows, dyadic radius rows, regular-rational handoff, selector rows,
transports, continuations, provenance, and local naming rows have been
displayed.

Finally apply the RegSeqRat product seal coverage theorem
\autoref{thm:cauchy-product-regseqrat-product-seal-coverage}. Agreement on the
displayed StreamName, dyadic, classifier, and Real seal boundary rows therefore
forces both consumers to inspect the same finite product-route surface. The
cited coverage theorem also lists the missing coordinates, so no host
multiplication, quotient product, selected limit, trichotomy row, or ambient
completeness object can be introduced by reusing the selector.
\end{proof}

\begin{theorem}[CauchyProduct Real seal selector coherence]
\label{thm:cauchy-product-real-seal-selector-coherence}
Let two accepted $\CauchyProductUp$ packets use the same finite
observation-budget selector. Suppose their paired $\StreamNameUp$ windows,
$\DyadicRatCoreUp$ radius and observation rows, $\RegSeqRatUp$ classifier row,
and $\RealUp$ seal boundary agree componentwise on the public packet rows. Then
every Real-seal consumer and every $\CauchyLimitSealUp$ sibling-seal consumer
reads the same finite route
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the shared selector rows. Selector reuse is coherent with the full
L10 sibling seal route, and it exports no host multiplication, quotient stream,
selected limit, trichotomy row, choice witness, or ambient completeness datum.
\end{theorem}
\begin{proof}
First read the Real-seal side through
\autoref{thm:cauchy-product-real-seal-upstream-dependency}. That theorem
exhausts every completion-facing Real-seal read by the displayed route, together
with accepted observation-budget rows, before the $\RealUp$ boundary can be
consumed.

Next read the sibling-seal side through
\autoref{thm:cauchy-product-limitseal-sibling-dependency}. It identifies the
$\CauchyLimitSealUp$ compatibility boundary as a horizontal consumer of the same
StreamName, dyadic, classifier, Real, transport, route, package, and local naming
rows, so the sibling edge has no independent analytic coordinate.

Finally apply
\autoref{thm:cauchy-product-shared-selector-real-seal-associativity}. Since the
two accepted packets share one selector and agree on the public window, radius,
observation, classifier, and Real boundary rows, selector reuse fixes the finite
product-route surface for both packets. Combining the three cited theorems gives
the same route for Real-seal and $\CauchyLimitSealUp$ consumers, with no host
multiplication, quotient streams, selected limits, trichotomy, choice, or ambient
completeness.
\end{proof}

\begin{theorem}[CauchyProduct limit-seal selector coherence]
\label{thm:cauchy-product-limitseal-selector-coherence}
Let an accepted $\CauchyProductUp$ packet reuse the same finite observation-budget selector for its Real-seal route and for the sibling route consumed through \autoref{ch:concrete-instances-cauchylimitseal-namecert}. Then the selector remains coherent on the displayed product route
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and on the shared StreamName, dyadic, RegSeqRat, Real-boundary, transport, route, package, and local NameCert rows. The sibling edge adds no quotient stream, selected product limit, host multiplication coordinate, choice witness, or ambient completeness datum.
\end{theorem}
\begin{proof}
Read the Real-seal route through \autoref{thm:cauchy-product-real-seal-selector-coherence}. The selector already fixes the finite product-route surface for every Real-seal consumer that agrees on the public StreamName, dyadic, classifier, and Real-boundary rows.

Now read the sibling consumer through \autoref{ch:concrete-instances-cauchylimitseal-namecert}. The CauchyLimitSeal boundary consumes the same finite stream windows, dyadic observations, regular classifier row, Real boundary, transports, routes, package provenance, and local naming rows.

Thus the reused selector is not a new analytic coordinate. It is a shared finite witness for the same displayed product-route surface, and the sibling handoff cannot export quotient streams, selected product limits, host multiplication, choice, or ambient completeness because none of those rows is present in either route.
\end{proof}

\begin{lemma}[CauchyProduct Real seal selector minimal witness]
\label{lem:cauchy-product-real-seal-selector-minimal-witness}
For a completion-facing consumer of an accepted $\CauchyProductUp$ Real-seal packet, the local admission and consumption claim is witnessed by the single displayed product route
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the shared $\FiniteObservationBudgetSelectorUp$ rows when the consumer asks for a selector. If a consumer presents a larger reading of the same Real-seal claim, then its accepted part factors through this displayed witness: the source admission uses only $X,Y,W_X,W_Y$, the budget and product admission uses only $M_X,M_Y,Q_X,Q_Y,P,L$, the classifier admission uses only $E$, and the seal consumption uses only $H,C,N$ with the displayed Real boundary. No unlisted quotient stream, selected product limit, host multiplication primitive, trichotomy row, independent real carrier, ambient choice object, or ambient completeness witness can serve as an additional admission coordinate.
\end{lemma}
\begin{proof}
Start with the upstream dependency theorem \autoref{thm:cauchy-product-real-seal-upstream-dependency}. It states that every completion-facing Real-seal read first consumes the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the product budget ledger, the $\RegSeqRatUp$ classifier row, and the $\RealUp$ seal surface. In coordinates this is exactly the displayed packet, with accepted observation-budget rows only when a budget consumer asks for them.

Now apply the shared-selector Real-seal stability theorem \autoref{thm:cauchy-product-shared-selector-real-seal-associativity}. When two accepted product packets read their factor windows through the same $\FiniteObservationBudgetSelectorUp$ route and agree on the public window, radius, classifier, and Real-boundary rows, every multiplication-facing Real-seal consumer reads the same finite product-route surface together with the shared selector rows. Thus selector reuse does not create a second product seal surface; it only names the finite selector rows already attached to the displayed route.

Combine the two readings by sorting the consumer-facing coordinates by their role in the displayed packet. The source part is forced to factor through $X,Y,W_X,W_Y$ by the upstream source admission. The budget and product part is forced to factor through $M_X,M_Y,Q_X,Q_Y,P,L$ before the classifier is visible. The classifier part is forced to factor through $E$, and the final seal handoff is carried by $H,C,N$ together with the Real boundary already listed by the two cited theorems. The shared selector rows may be consumed as witness rows for the common observation-budget route, but they do not add any unlisted analytic object.

Therefore any larger accepted reading has the same consumer-facing content after projection to the displayed product route and the shared selector rows. Since both cited theorems explicitly exclude quotient streams, selected limits, host multiplication primitives, trichotomy rows, independent real carriers, ambient choice objects, and ambient completeness witnesses from the exported route, none of those objects can be used as an additional admission or consumption coordinate.
\end{proof}

\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_selector\_minimal\_witness}
