\begin{theorem}[CauchyProduct shared-window root admission]
\label{thm:cauchy-product-shared-window-root-admission}
Every accepted $\CauchyProductUp$ packet admits a root-facing product route only through the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ readback row, the $\RealUp$ seal, and the support rows $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The admitted root surface is
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
It exposes no product before those paired finite windows and their dyadic observations have been read.
\end{theorem}
\begin{proof}
Begin with the CauchyProduct StreamName handoff. It places the product route downstream of the paired source-window rows $W_X,W_Y$ and their modulus rows $M_X,M_Y$.

Next use the product-observation seal obligations and ledger exhaustion. These rows force the dyadic observations $Q_X,Q_Y$, the product observation $P$, and the product-radius ledger $L$ to be read before the $\RegSeqRatUp$ classifier row $E$ is available.

Finally pass through the Real multiplication seal handoff and the public consumer boundary. The rows $H,C,L,N$ preserve, route, account for, and name the same packet, so a root-facing consumer receives the product only through the displayed finite window inventory.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_shared\_window\_root\_admission}

\begin{theorem}[CauchyProduct root window RegSeqRat seal route]
\label{thm:cauchyproduct-root-window-regseqrat-seal-route}
Every accepted $\CauchyProductUp$ root route that reaches a $\RegSeqRatUp$ or $\RealUp$ consumer reads the paired $\StreamNameUp$ windows, the paired $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ readback row, and the $\RealUp$ seal in that order. The route is the finite inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and it exposes no product-facing seal before the paired windows and dyadic observations have been recorded.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_window\_regseqrat\_seal\_route}
\begin{proof}
Begin with \autoref{thm:cauchy-product-shared-window-root-admission}. It admits a root-facing product route only after the paired window rows $W_X,W_Y$, source-radius rows $M_X,M_Y$, and dyadic observation rows $Q_X,Q_Y$ have entered the product packet.

Next use the product-observation and ledger rows later in this chapter. The paired-window regularity exhaustion, root factor-source exhaustion, and root budget classifier coverage keep the product row $P$, classifier row $E$, and ledger row $L$ downstream of the same finite window and dyadic observation route.

Finally apply the Real seal root surface and seal-ledger exactness. These rows place the $\RealUp$ seal after the $\RegSeqRatUp$ readback and preserve the same $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ evidence, giving the stated order with no additional analytic coordinate.
\end{proof}

\begin{theorem}[CauchyProduct root budget non-escape]
\label{thm:cauchyproduct-root-budget-nonescape}
An accepted $\CauchyProductUp$ root formation packet cannot export quotient streams, host real multiplication, ambient completeness, selected limits, trichotomy rows, independent real carriers, or unbounded selector rows. Every exported product route is confined to paired finite windows, dyadic observations, product-observation rows, the $\RegSeqRatUp$ classifier, the $\RealUp$ seal, displayed transport, displayed continuation, package provenance, local naming, and any explicitly displayed $\RealObservationBudgetUp$ rows.
\end{theorem}
\begin{proof}
Start from the shared-window root admission route. It places the product behind the paired finite windows, dyadic observations, classifier row, seal row, and local support rows.

Use the later product-observation and budget rows to account for all consumers. The budgeted readback root boundary and budgeted product consumer boundary add only displayed $\RealObservationBudgetUp$ rows, while paired-window regularity exhaustion and root budget classifier coverage keep every product read inside the same finite ledger.

The excluded objects have no coordinate in this inventory. Since quotient streams, host real multiplication, ambient completeness, selected limits, trichotomy rows, independent real carriers, and unbounded selector rows are absent from the packet and absent from the budget handoff, root formation cannot export them.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_budget\_nonescape}

\begin{theorem}[CauchyProduct root selector-ledger exactness]
\label{thm:cauchyproduct-root-selector-ledger-exactness}
Every selector or budget row used by a downstream $\CauchyProductUp$ product consumer is recorded in the local ledger before the consumer reads the $\RealUp$ seal. The recorded route includes the paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, product row, $\RegSeqRatUp$ readback, $\RealUp$ seal, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, local $\NameCert$ evidence, and any displayed $\RealObservationBudgetUp$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_selector\_ledger\_exactness}
\begin{proof}
First apply shared-window root admission. It fixes the product route as a finite sequence through paired windows, dyadic observations, product formation, classifier readback, transport, continuation, ledger, provenance, and local naming rows.

Next attach the downstream consumer. The budgeted readback root boundary, root seal-ledger exactness, and budgeted product consumer boundary require any budget-facing read to carry its displayed observation-budget rows with the same product ledger.

Finally read the seal. The Real seal root surface and Real seal multiplication non-escape rows leave the consumer no route around the local ledger, so each selector or budget row has already been recorded before the $\RealUp$ seal is consumed.
\end{proof}

\begin{theorem}[CauchyProduct budgeted readback root boundary]
\label{thm:cauchy-product-budgeted-readback-root-boundary}
For an accepted $\CauchyProductUp$ packet feeding an accepted $\RealObservationBudgetUp$ packet, every root-facing readback of the product factors through the product inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and the budget inventory
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
The readback reaches the $\RegSeqRatUp$ and $\RealUp$ rows only after the paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows have been consumed.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_budgeted\_readback\_root\_boundary}
\begin{proof}
First apply the shared-window root admission theorem. It binds the product route to the paired finite windows, dyadic observations, product observation, classifier row, Real seal, transport, continuation, ledger, provenance, and local naming rows.

Now enter the observation budget. The Real observation budget handoff and observation-budget RegSeq handoff require the budget rows $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$ before a downstream consumer may read the regular-sequence or real-facing product.

The budgeted product consumer boundary then identifies the complete readback interface. Since both inventories are finite packet rows, there is no coordinate for reading the product through a quotient stream, host multiplication primitive, selected limit, trichotomy row, independent real carrier, or ambient completeness witness.
\end{proof}

\begin{theorem}[CauchyProduct Real seal root surface]
\label{thm:cauchy-product-real-seal-root-unblock-surface}
The $\RealUp$ seal surface of an accepted $\CauchyProductUp$ packet is root-visible only as the finite route composed from paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, $\RegSeqRatUp$ readback, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ evidence. When the packet feeds an accepted $\RealObservationBudgetUp$ packet, the same route is read through the budgeted boundary of \autoref{thm:cauchy-product-budgeted-readback-root-boundary}.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_root\_unblock\_surface}
\leanvariant{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_root\_surface}
\begin{proof}
Start with the Real multiplication seal handoff. It makes the real-facing product row depend on the $\RegSeqRatUp$ classifier $E$ rather than on host multiplication or a selected real representative.

Trace $E$ back through the finite product route. The CauchyProduct StreamName handoff, product-observation seal obligations, radius ledger, and radius product regularity force the route through $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,L$.

Finally compose with the budgeted readback root boundary. The budget packet reads the same real seal through $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$, while the support rows preserve the product route as $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. Thus the root-visible Real seal is exactly the finite packet route.
\end{proof}

\begin{theorem}[CauchyProduct RealAlgOrder product-observation export]
\label{thm:cauchy-product-realalgorder-product-observation-export}
Every $\RealAlgOrderUp$ multiplication export that reads an accepted $\CauchyProductUp$ packet factors through the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ classifier, the $\RealUp$ seal, the $\RealObservationBudgetUp$ rows when a budget packet serves the read, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The export reads multiplication only as the finite product-observation route
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B
$$
when they are present. It exports no host multiplication, quotient stream, selected limit, trichotomy, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_realalgorder\_product\_observation\_export}
\begin{proof}
First compose root-window admission with the budgeted readback boundary. The paired $\StreamNameUp$ windows and $\DyadicRatCoreUp$ observations must be read before the product row, classifier row, and seal row are visible to any downstream multiplication consumer.

Next apply the Real seal root surface. It keeps the real-facing product on the finite route through $\RegSeqRatUp$, $\RealUp$, displayed $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row.

Finally route the same surface through the observation-budget rows when the budget packet serves the read. Since the product and budget inventories contain no host multiplication primitive, quotient stream, selected limit, trichotomy branch, independent real carrier, or ambient completeness witness, the $\RealAlgOrderUp$ export can read only the displayed product-observation route.
\end{proof}

\begin{theorem}[CauchyProduct dyadic-radius ledger handoff]
\label{thm:cauchy-product-dyadic-radius-ledger-handoff}
For an accepted $\CauchyProductUp$ packet feeding an accepted $\RealObservationBudgetUp$ packet, the input-radius rows and the product-radius ledger rows are preserved when the product packet hands off to the observation-budget packet. The handoff carries
$$
M_X,M_Y,Q_X,Q_Y,L
$$
through the product route
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and into the budget route
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
It preserves the displayed dyadic-radius accounting and exports no host multiplication, quotient stream, selected limit, trichotomy, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_dyadic\_radius\_ledger\_handoff}
\begin{proof}
Start with root-window admission. The input-radius rows and dyadic observations enter the product packet together with the paired finite windows, so the product route cannot reach $P$ or $E$ without first reading $M_X,M_Y,Q_X,Q_Y$.

Use radius budget conservation for the product side. It identifies $L$ as the finite ledger that carries the input-radius and product-radius accounting through componentwise $\hsame$ and displayed $\Cont$ routes.

Now pass through the Real seal root surface and the budgeted readback boundary. The observation-budget packet reads the same classifier and seal route through its displayed rows $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$, preserving the dyadic-radius ledger rather than replacing it by any excluded analytic object.
\end{proof}

\begin{theorem}[CauchyProduct root-window factorization]
\label{thm:cauchy-product-root-window-factorization}
Every accepted product consumer that enters through a $\CauchyProductUp$ packet factors through the root-window rows
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
before any $\RealObservationBudgetUp$ row is read. The factorization route first reads the two $\StreamNameUp$ window schedules, then the paired dyadic observations and radius ledgers, then the product row $P$, the $\RegSeqRatUp$ classifier row $E$, the displayed $\hsame$ transports, the $\Cont$ routes, the ledger row $L$, and the local $\NameCert_{\CauchyProductUp}$ row $N$. It exposes no quotient stream, selected limit, trichotomy, host multiplication primitive, independent real carrier, or ambient completeness coordinate before the budget packet is entered.
\end{theorem}
\begin{proof}
Start with the StreamName handoff. It makes the product consumer read the paired finite windows $W_X,W_Y$, moduli $M_X,M_Y$, and dyadic observations $Q_X,Q_Y$ as displayed packet rows rather than as ambient streams.

Next use paired-window closure and the product ledger. The pointwise product row $P$ and classifier row $E$ are reached only through the paired finite windows, radius accounting, and regular-rational route; the displayed $\hsame$ and $\Cont$ rows carry the same route without adding another analytic carrier.

Finally apply \autoref{thm:cauchy-product-budget-product-consumer-boundary}. That boundary places every later observation-budget read downstream of the product inventory, so the root window has already factored through $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$ before any budget row is available.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_window\_factorization}

\begin{theorem}[CauchyProduct radius budget conservation]
\label{thm:cauchy-product-radius-budget-conservation}
For an accepted $\CauchyProductUp$ packet feeding an accepted $\RealObservationBudgetUp$ packet, the paired input-radius rows and the product-radius row are conserved under componentwise $\hsame$ and displayed $\Cont$ routes through the budget packet. Thus the route from
$$
M_X,M_Y,Q_X,Q_Y,L
$$
to the budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B
$$
preserves the same finite radius ledger, the same product-radius witness, and the same regular-sequence classifier handoff; it cannot replace them by a selected limit, quotient-stream equality, host multiplication estimate, trichotomy branch, independent real carrier, or ambient completeness statement.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_radius\_budget\_conservation}
\begin{proof}
First read the radius ledger on the product side. Ledger exhaustion and radius product regularity identify the input radii, the dyadic product observation, and the product-radius row as the exact finite accounting surface for the $\RegSeqRatUp$ classifier.

Now transport that surface componentwise. The displayed $\hsame$ rows preserve the left and right input-radius rows, while the displayed $\Cont$ routes preserve the product-radius route and package provenance inside the finite packet.

Pass the conserved ledger through the observation budget. The observation-budget RegSeq handoff reads the same classifier route as $R_B$ together with $H_B,C_B,P_B,N_B$, and \autoref{thm:cauchy-product-budget-product-consumer-boundary} leaves no coordinate by which an analytic replacement could enter.
\end{proof}

\begin{theorem}[CauchyProduct shared-tail budget consumer]
\label{thm:cauchy-product-shared-tail-budget-consumer}
Let an accepted $\CauchyProductUp$ packet be consumed by an accepted $\RealObservationBudgetUp$ packet, and suppose the paired source windows are admitted through the shared threshold surface of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}. Then every seal-facing product consumer factors through the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ classifier, the product-radius budget rows, the shared RegularCauchyTailMeet threshold, and the $\RealUp$ seal rows before any product consumer may read the seal.

The complete consumer route is the product inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the budget inventory
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
It exposes no quotient stream, selected limit, host multiplication, trichotomy, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_shared\_tail\_budget\_consumer}
\begin{proof}
First compose the root-window factorization with the shared tail surface. The factorization forces every product read through $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$, while \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert} supplies the common finite threshold used by the paired source windows.

Next apply radius budget conservation. The rows $M_X,M_Y,Q_X,Q_Y,L$ remain the same finite radius ledger when the product route is transported through the observation-budget packet.

Now use the budgeted readback root boundary. It attaches $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$ to the same product route and makes the $\RegSeqRatUp$ classifier and $\RealUp$ seal readable only after the paired windows, dyadic observations, budget rows, and shared threshold have been displayed.

Finally apply the sibling tail-meet threshold surface together with the budgeted product consumer boundary. The resulting route has no remaining coordinate for a quotient stream, selected limit, host multiplication, trichotomy, independent real carrier, or ambient completeness principle, so the seal consumer is exactly the shared-tail budget consumer described above.
\end{proof}

\begin{theorem}[CauchyProduct tail-fusion budget route]
\label{thm:cauchy-product-tail-fusion-budget-route}
Every accepted $\CauchyProductUp$ product consumer that also consumes $\RegularCauchyTailFusionUp$ and $\RegularCauchyTailBudgetUp$ factors through the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ readback, the fusion shared-threshold row, and the tail-budget row before the $\RealUp$ seal is read. The root-visible route is the product inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the observation-budget inventory
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B
$$
and the displayed tail-fusion and tail-budget rows supplied by the sibling certificates. Its support is carried only by $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; it exports no quotient stream, host multiplication, selected limit, trichotomy row, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_tail\_fusion\_budget\_route}
\begin{proof}
First use shared-window root admission. The accepted product consumer must read the paired $\StreamNameUp$ windows and $\DyadicRatCoreUp$ observations before the product row, classifier row, ledger row, or seal row can be visible.

Next attach the tail-fusion surface. The $\RegularCauchyTailFusionUp$ consumer contributes its shared-threshold row as a displayed finite route over the same source windows, so the product read cannot fork into an independent stream or carrier.

Finally compose with \autoref{thm:cauchy-product-shared-tail-budget-consumer}. The tail-budget packet reads the same product inventory and observation-budget inventory, while $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ preserve and name the route. The listed excluded objects have no coordinate in any of the composed packets.
\end{proof}

\begin{theorem}[CauchyProduct root budget-fusion non-escape]
\label{thm:cauchy-product-root-budget-fusion-nonescape}
For an accepted $\CauchyProductUp$ product consumer served through $\RegularCauchyTailFusionUp$ and $\RegularCauchyTailBudgetUp$, the root-visible budget-fusion route is exhausted by the paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, $\RegSeqRatUp$ readback, fusion shared-threshold row, tail-budget row, $\RealUp$ seal, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. No consumer of this route can recover a quotient stream, host multiplication primitive, selected limit, trichotomy row, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-product-tail-fusion-budget-route}. It gives the complete product, observation-budget, tail-fusion, and tail-budget inventory seen by the root-facing consumer.

Now apply radius budget conservation. The input-radius rows, dyadic observations, product-radius ledger, and regular readback row remain the same finite accounting surface when the route enters the tail-budget consumer.

The non-escape conclusion is then coordinate exhaustion. The composed packets expose only the displayed windows, observations, readback, threshold, budget, seal, transport, route, provenance, and local naming rows, so none of the excluded analytic objects can be read from the root-visible route.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_budget\_fusion\_nonescape}

\begin{theorem}[CauchyProduct RealAlgOrder root handoff]
\label{thm:cauchy-product-realalgorder-root-handoff}
Every $\RealAlgOrderUp$ product consumer that reads an accepted $\CauchyProductUp$ packet through $\RegularCauchyTailFusionUp$ and $\RegularCauchyTailBudgetUp$ receives only the root-visible budget-fusion route of \autoref{thm:cauchy-product-tail-fusion-budget-route}. Thus the RealAlgOrder multiplication observation is consumed through paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, $\RegSeqRatUp$ readback, the fusion shared-threshold row, the tail-budget row, the $\RealUp$ seal, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, with no host multiplication, quotient stream, selected limit, trichotomy, independent real carrier, or ambient completeness coordinate exported.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchy-product-realalgorder-product-observation-export}. The $\RealAlgOrderUp$ multiplication export reads multiplication only as the finite product-observation route, with observation-budget rows when the budget packet serves the read.

Next compose the export with \autoref{thm:cauchy-product-tail-fusion-budget-route}. This inserts the shared tail-fusion threshold and tail-budget rows before the seal-facing RealAlgOrder read without adding a second multiplication carrier.

Finally use \autoref{thm:cauchy-product-root-budget-fusion-nonescape}. Since the composed route has no coordinate for host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, or ambient completeness, the RealAlgOrder handoff is exactly the displayed root-visible budget-fusion route.
\end{proof}

\begin{theorem}[CauchyProduct RegSeq seal non-escape]
\label{thm:cauchy-product-regseq-seal-nonescape}
A $\RegSeqRatUp$ or $\RealUp$ seal consumer that is reached from an accepted $\CauchyProductUp$ packet and an accepted $\RealObservationBudgetUp$ packet cannot replace the finite product classifier by host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, or ambient completeness. The only available seal-facing route is the product inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the observation-budget inventory
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_regseq\_seal\_nonescape}
\begin{proof}
Begin at the product seal. The Real multiplication seal handoff reads the product classifier $E$ through the StreamName windows, dyadic observations, radius ledger, displayed transports, continuations, provenance, and local $\NameCert$ row.

Next enter the observation budget. The Real observation budget handoff and the observation-budget RegSeq handoff make the budget consumer read the classifier only as a finite budget row, with the same transports, routes, provenance, and local naming evidence.

The budgeted product consumer boundary then seals the route. Since the displayed product and budget inventories are complete, there is no remaining packet coordinate for host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyProduct budgeted product associative route]
\label{thm:cauchy-product-budget-product-associative-route}
Let two accepted $\CauchyProductUp$ packets feed a common accepted $\RealObservationBudgetUp$ packet, and suppose the displayed source windows, dyadic observations, product-radius ledgers, $\RegSeqRatUp$ classifier rows, $\RealUp$ seal rows, budget rows, transports, routes, provenance, and local naming rows are the same:
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
Then the finite seal-facing route seen by the budgeted product consumer is the same whether the product observation is grouped as first-left-then-right or first-right-then-left. The comparison is a route-composition equality inside the displayed row inventory; it does not introduce quotient streams, host multiplication primitives, selected limits, trichotomy rows, independent real carriers, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_budget\_product\_associative\_route}
\begin{proof}
Begin with the common product inventory. The CauchyProduct StreamName handoff fixes the paired source-window reads, while ledger exhaustion and radius product regularity fix the product-radius and classifier route from the same displayed dyadic observations.

Pass both groupings through the Real-facing rows. The Real multiplication seal handoff and the Real observation budget handoff read the same $\RealUp$ seal rows and the same budget packet before any consumer-facing seal is exposed.

Finally compare the two composites. The observation budget RegSeq handoff and \autoref{thm:cauchy-product-budget-product-consumer-boundary} leave only the displayed product rows and budget rows available to the consumer. Since both groupings use exactly those rows with the same transports, routes, provenance, and local names, their seal-facing finite routes coincide within the packet inventory.
\end{proof}

\begin{theorem}[CauchyProduct budgeted product symmetric route]
\label{thm:cauchy-product-budget-product-symmetric-route}
For an accepted $\CauchyProductUp$ packet feeding an accepted $\RealObservationBudgetUp$ packet, swapping the two source-window families swaps only
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y
$$
between the two product inputs. The budget rows $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$, classifier row $E$, Real seal handoff, displayed transports, routes, provenance, and local $\NameCert_{\CauchyProductUp}$ row are preserved as the same finite consumer surface. No symmetric route exports quotient streams, host multiplication primitives, selected limits, trichotomy rows, independent real carriers, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_budget\_product\_symmetric\_route}
\begin{proof}
Read the two source families through the CauchyProduct StreamName handoff. Swapping the sources exchanges only the displayed left and right window, modulus, and dyadic observation rows.

The product-radius ledger and radius product regularity are then replayed with the exchanged source rows. They still produce the same classifier-facing product ledger and route to $E$, because no additional analytic coordinate is available in the packet.

Route the result through the Real multiplication seal handoff, the Real observation budget handoff, and the observation budget RegSeq handoff. The budget packet, seal handoff, transports, continuations, provenance, and local naming rows are unchanged, so \autoref{thm:cauchy-product-budget-product-consumer-boundary} gives the same consumer boundary with only the two source families exchanged.
\end{proof}

\begin{theorem}[CauchyProduct budgeted product unit route]
\label{thm:cauchy-product-budget-product-unit-route}
If one displayed source of an accepted $\CauchyProductUp$ packet is the regular-Cauchy unit source, then inserting that unit source contributes only its unit source rows to the finite packet. The budgeted product consumer still reads the same product boundary
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
together with the same observation-budget boundary
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B,
$$
with the unit source occupying the corresponding source-window, modulus, and dyadic observation coordinates. The route does not export quotient streams, host multiplication primitives, selected limits, trichotomy rows, independent real carriers, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_budget\_product\_unit\_route}
\begin{proof}
Insert the displayed unit source as one regular-Cauchy input. Its contribution is read through the same CauchyProduct StreamName handoff as any other source: one window family, one modulus row, and one dyadic observation family.

Ledger exhaustion and radius product regularity then place the unit rows in the product-radius ledger. The route still reaches the $\RegSeqRatUp$ classifier and $\RealUp$ seal through the existing product packet rather than through a host multiplication primitive or selected limit.

The Real observation budget handoff and observation budget RegSeq handoff carry the result into the same budget packet. By \autoref{thm:cauchy-product-budget-product-consumer-boundary}, the consumer boundary is unchanged except for the displayed unit rows occupying their source slots, and all excluded analytic objects remain outside the finite inventory.
\end{proof}

\begin{theorem}[CauchyProduct paired-window regularity exhaustion]
\label{thm:cauchy-product-paired-window-regularity-exhaustion}
Every accepted $\CauchyProductUp$ packet whose product read is consumed by a $\RegSeqRatUp$ or $\RealUp$ route factors through exactly the finite rows
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
The factorization first binds the paired source windows $W_X,W_Y$, the source-radius rows $M_X,M_Y$, and the dyadic observations $Q_X,Q_Y$; then it reads the product row $P$ and the product-radius route that supplies the classifier row $E$; finally it transports the sealed product through $H,C,L,N$ to the consumer boundary. The route excludes host multiplication, quotient streams, selected limits, trichotomy, independent real carriers, and ambient completeness.
\end{theorem}
\begin{proof}
Start with paired-window closure. It forces any accepted product read to pass through $W_X,W_Y$ before exposing $M_X,M_Y,Q_X,Q_Y$, the product row $P$, and the downstream classifier route.

Next use radius product regularity. The product-radius ledger is the only route from the displayed dyadic product observation to the $\RegSeqRatUp$ classifier $E$, so the regularity witness is part of the finite packet rather than an external multiplication or completeness claim.

Now pass to the seal-facing boundary. The Real multiplication seal handoff and the RealCompleteness diagonal seal route make every $\RealUp$ or diagonal consumer read only the displayed classifier, transports, continuation rows, ledger, package provenance, and local $\NameCert_{\CauchyProductUp}$ evidence.

Finally apply ledger exhaustion. Since the named rows exhaust the accepted packet, there is no remaining coordinate for quotient streams, selected limits, trichotomy, independent real carriers, ambient completeness, or a host multiplication primitive.
\end{proof}

\begin{theorem}[CauchyProduct root factor-source exhaustion]
\label{thm:cauchy-product-root-factor-source-exhaustion}
Every accepted $\CauchyProductUp$ route that exposes the product row $P$ to a downstream $\RegSeqRatUp$, $\RealUp$, or $\RealObservationBudgetUp$ consumer first exhausts the two factor sources through
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y.
$$
The packet therefore reads the left and right $\StreamNameUp$ windows, the two source-radius rows, and the two $\DyadicRatCoreUp$ observation rows before $P$ is visible. The product route has no source-facing coordinate for quotient streams, selected limits, host multiplication, trichotomy, independent real carriers, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_factor\_source\_exhaustion}
\begin{proof}
Start from the paired-window regularity exhaustion theorem. It orders every accepted product read by the displayed rows $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$, with the source windows and dyadic observations preceding the product row.

Next apply the root-window factorization and budgeted readback boundary. These keep the same source rows when the product is read through a budget packet, so $P$ cannot be inspected before the two factor windows, radius rows, and dyadic observations have been consumed.

Finally pass through the Real seal root surface. The seal handoff reads the product only after the classifier and transport rows have inherited the exhausted source inventory, leaving no separate analytic object from which $P$ could be imported.
\end{proof}

\begin{theorem}[CauchyProduct root budget classifier coverage]
\label{thm:cauchy-product-root-budget-classifier-coverage}
The product observation $P$, the product-radius ledger $L$, and the $\RegSeqRatUp$ classifier row $E$ of an accepted $\CauchyProductUp$ packet are covered only by the dyadic-radius budget route through $\DyadicRatCoreUp$ and $\RegSeqRatUp$. More explicitly, any consumer that reaches one of $P,L,E$ must read the finite product inventory
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and, when an observation budget is present, the finite budget inventory
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
No independent classifier, host multiplication estimate, quotient-stream comparison, selected limit, trichotomy row, independent real carrier, or ambient completeness witness covers $P,L,E$.
\end{theorem}
\begin{proof}
First use radius budget conservation. It identifies the route from the two dyadic source observations to the product-radius ledger and then to the regular-sequence classifier, so $P,L,E$ stay on the same dyadic-radius accounting path.

Next combine this with paired-window regularity exhaustion. The product row $P$ is reached only after the paired windows, source-radius rows, and dyadic observations have been read, and the classifier row $E$ is supplied by the product-radius route rather than by an external real carrier.

When the read is budgeted, apply the budgeted readback root boundary and the budgeted product consumer boundary. They add exactly the displayed $\RealObservationBudgetUp$ rows and do not add a second route for $P,L,E$.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_budget\_classifier\_coverage}

\begin{theorem}[CauchyProduct root seal-ledger exactness]
\label{thm:cauchy-product-root-seal-ledger-exactness}
Any $\RealUp$ or $\RealObservationBudgetUp$ seal consumer of an accepted $\CauchyProductUp$ packet reads exactly the joined product and budget ledger rows
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and, when a budget packet is present,
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
The seal consumer cannot import quotient streams, selected limits, host multiplication, trichotomy, independent real carriers, ambient completeness, or any row outside this joined ledger.
\end{theorem}
\begin{proof}
Begin with the Real seal root surface. It routes the real-facing product through paired windows, dyadic observations, the $\RegSeqRatUp$ readback row, displayed transports, displayed continuations, package provenance, and local $\NameCert$ evidence.

Next apply root factor-source exhaustion and root budget classifier coverage. The first fixes the factor-source rows before $P$ can be read; the second fixes the only dyadic-radius route covering $P,L,E$ and, when present, the exact budget rows.

Finally use the budgeted product consumer boundary. Since the product ledger and the observation-budget ledger are already the complete finite inventories, a $\RealUp$ or $\RealObservationBudgetUp$ seal consumer has no remaining row from which to import quotient streams, selected limits, host multiplication, trichotomy, independent real carriers, or ambient completeness.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_seal\_ledger\_exactness}

\begin{theorem}[CauchyProduct budgeted bilinear diagonal]
\label{thm:cauchy-product-budgeted-bilinear-diagonal}
Let two accepted $\RegSeqRatUp$-backed $\CauchyProductUp$ factors share a $\RealObservationBudgetUp$ packet and a $\DyadicRatCoreUp$ radius ledger. Then the diagonal product window is determined by the existing paired-window and budgeted product routes over
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and the observation-budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
The resulting diagonal read is bilinear only as a finite product-observation certificate: it exposes the two regular source windows, the dyadic radius rows, the pointwise product row, the shared budget ledger, the $\RegSeqRatUp$ classifier, and the $\RealUp$ seal handoff, and it exports no host multiplication primitive, quotient stream equality, selected limit, independent real carrier, or ambient completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-product-paired-window-regularity-exhaustion}. It forces the product read through the two source windows, source-radius rows, dyadic observations, product row, classifier row, transports, continuations, ledger, package provenance, and local naming row.

Next apply the budgeted product route supplied by \autoref{thm:cauchy-product-budget-product-consumer-boundary}. The shared observation budget contributes exactly $E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B$, so the product read and the budget read meet on the same diagonal request rather than on a host arithmetic operation.

Use the radius budget conservation route of \autoref{thm:cauchy-product-radius-budget-conservation}. The dyadic radius ledger records the bound consumed by the product window, so the diagonal product observation is determined by the displayed source windows and the displayed budget rows.

Finally use the Real multiplication seal handoff. The seal receives only the finite product and budget rows already listed, giving the stated bilinear diagonal certificate without quotient streams, selected limits, independent real carriers, host multiplication, or ambient completeness.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_budgeted\_bilinear\_diagonal}

\begin{theorem}[CauchyProduct shared-radius product coverage]
\label{thm:cauchy-product-shared-radius-product-coverage}
Every displayed product-observation request consumed by the $\RealAlgOrderUp$ multiplication export is covered by paired-window regularity plus radius-budget conservation. Concretely, a multiplication consumer can read a $\CauchyProductUp$ product observation only through the two $\RegularCauchyNameUp$ source rows, their shared $\StreamNameUp$ windows, the displayed $\DyadicRatCoreUp$ radius observations, the $\RealObservationBudgetUp$ budget rows, the $\RegSeqRatUp$ classifier, the $\RealUp$ seal handoff, and the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchy-product-paired-window-regularity-exhaustion}. Any product read reaching a regular-sequence or real-facing consumer already passes through the paired windows and the dyadic product-radius rows.

Apply \autoref{thm:cauchy-product-budgeted-bilinear-diagonal}. The shared observation budget aligns the product request with the same finite diagonal window and the same radius ledger, so a multiplication export receives a covered product observation rather than an implicit arithmetic operation.

Now use the Real seal handoff and the RegSeq seal non-escape route recorded earlier in this chapter. These rows keep the public consumer inside the product packet, budget packet, classifier row, seal row, transports, continuations, package provenance, and local naming certificate.

Thus every product-observation request displayed to the $\RealAlgOrderUp$ multiplication export is accounted for by paired-window regularity and radius-budget conservation, with no hidden multiplication or ambient completeness route.
\end{proof}

\begin{theorem}[CauchyProduct Real seal multiplication non-escape]
\label{thm:cauchy-product-real-seal-multiplication-nonescape}
The public multiplication consumer of a $\CauchyProductUp$ packet receives only the finite $\CauchyProductUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealObservationBudgetUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed by the product and budget certificates. It receives no host multiplication primitive, quotient stream equality, selected limit, trichotomy row, independent real carrier, ambient completeness principle, or unrecorded radius witness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-product-shared-radius-product-coverage}. It says that every multiplication-facing product observation is covered by the paired source windows, dyadic radius rows, shared observation budget, classifier route, and real seal handoff.

Use \autoref{thm:cauchy-product-budget-product-consumer-boundary} to identify the public budget boundary. The consumer can inspect the product packet and the observation-budget packet, but only through their displayed rows and the recorded transport, continuation, provenance, and local naming routes.

Finally apply the paired-window exhaustion theorem and the RegSeq seal non-escape route. They leave no coordinate for host multiplication, quotient stream equality, selected limits, trichotomy, independent real carriers, ambient completeness, or unrecorded radius witnesses, so the multiplication seal is exactly the finite public certificate stated above.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_seal\_multiplication\_nonescape}

\begin{theorem}[CauchyProduct root source admission]
\label{thm:cauchy-product-root-source-admission}
For every accepted $\CauchyProductUp$ packet, the source rows
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y
$$
admit a finite $\BHist$ root surface over $\RegularCauchyNameUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The surface is generated by the two regular-Cauchy source rows, the paired finite-window schedules, the paired radius rows, and the dyadic observation rows, and it exposes no quotient stream, selected limit, host multiplication primitive, ambient completeness row, trichotomy row, or independent real carrier.
\end{theorem}
\begin{proof}
Start with the packet source of \autoref{def:cauchy-product-namecert-source}. Its displayed coordinates put $X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y$ inside the same finite $\BHist$ packet as the product row, classifier row, transports, continuations, ledger, package provenance, and local naming row.

The sibling carriers supply the admissible readings. Use \autoref{ch:concrete-instances-streamname-namecert} for the finite window schedules, \autoref{ch:concrete-instances-dyadicratcore-namecert} for the dyadic observations and radius rows, \autoref{ch:concrete-instances-regseqrat-namecert} for the classifier route, and \autoref{ch:concrete-instances-real-namecert} for the real seal boundary.

Finally apply \autoref{thm:cauchy-product-root-window-obligations}, \autoref{thm:cauchy-product-root-budget-obligations}, and \autoref{thm:cauchy-product-root-real-seal-obligations}. These three obligations bind the source rows to finite windows, radius accounting, and the real-seal route, leaving no coordinate for any excluded analytic object.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_source\_admission}

\begin{theorem}[CauchyProduct root classifier stability]
\label{thm:cauchy-product-root-classifier-stability}
Componentwise classifier transport of the two source rows, paired windows, radius rows, dyadic observations, product observation, and $\RegSeqRatUp$ classifier preserves the same $\CauchyProductUp$ root packet
$$
X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
The transported packet is again routed only through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows over $\RegularCauchyNameUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$; it admits no quotient stream and no host multiplication primitive.
\end{theorem}
\begin{proof}
First read the source and window rows through \autoref{thm:cauchy-product-root-source-admission}. The theorem fixes the root source surface as a finite $\BHist$ packet over the listed sibling carriers.

Next transport the classifier componentwise. The StreamName and DyadicRatCore rows from \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-dyadicratcore-namecert} preserve the paired windows, radius rows, dyadic observations, and product observation through the displayed $\hsame$ and $\Cont$ data.

Now read the classifier and seal. The $\RegSeqRatUp$ and $\RealUp$ rows from \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}, together with \autoref{thm:cauchy-product-paired-window-regularity-exhaustion}, \autoref{thm:cauchy-product-radius-budget-conservation}, and \autoref{thm:cauchy-product-regseq-seal-nonescape}, keep the transported packet on the same finite route. Since the route is exhausted by the displayed packet, quotient streams and host multiplication primitives have no source row.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_classifier\_stability}

\begin{theorem}[CauchyProduct root product-row determinacy]
\label{thm:cauchy-product-root-product-row-determinacy}
For any two accepted $\CauchyProductUp$ root packets over the same displayed rows
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,H,C,L,N,
$$
the product row $P$ and classifier-facing row $E$ are determined by the paired finite-window route and the dyadic-observation route before the $\RegSeqRatUp$ readback and the $\RealUp$ seal are consumed. No host multiplication primitive, quotient stream, selected limit, trichotomy branch, independent real carrier, or ambient completeness coordinate can change $P$ or $E$ once those finite rows are fixed.
\end{theorem}
\begin{proof}
First read the common source surface through \autoref{thm:cauchy-product-root-source-admission}. The accepted packets expose the paired windows, radius rows, and dyadic observations as one finite $\BHist$ route over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next apply \autoref{thm:cauchy-product-paired-window-regularity-exhaustion}. It forces every product read toward a regular-rational or real-facing consumer through
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
Thus the rows preceding $P$ and $E$ already determine the multiplication-facing packet route.

Finally use \autoref{thm:cauchy-product-root-classifier-stability} together with the StreamName, DyadicRatCore, RegSeqRat, and Real carrier chapters \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. These routes preserve the same finite packet through componentwise transport, so the later $\RegSeqRatUp$ readback and $\RealUp$ seal can only consume the determined product and classifier-facing rows. The excluded analytic objects have no coordinate in the packet and cannot alter them.
\end{proof}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_product\_row\_determinacy}

\begin{theorem}[CauchyProduct root phase handoff]
\label{thm:cauchy-product-root-phase-handoff}
Every downstream L10 consumer of the $\CauchyProductUp$ root surface factors through the displayed paired windows, dyadic product route, radius ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal row, and local $\NameCert$ rows. Equivalently, the consumer boundary is the finite route through
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
and, when a budget packet is present, through the displayed budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
No downstream consumer receives a quotient stream, selected limit, host multiplication primitive, unrecorded radius witness, trichotomy branch, independent real carrier, or ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_root\_phase\_handoff}
\begin{proof}
Begin with the root packet. The source admission and classifier stability theorems keep $X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$ as one finite $\BHist$ surface over the sibling carriers named in \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

Next factor the product-facing consumer. Apply \autoref{thm:cauchy-product-shared-window-root-admission}, \autoref{thm:cauchy-product-budgeted-readback-root-boundary}, \autoref{thm:cauchy-product-real-seal-root-unblock-surface}, and \autoref{thm:cauchy-product-root-window-factorization}; these route the consumer through paired windows, dyadic observations, the product row, the classifier row, and the seal boundary.

Finally pass through the public multiplication surface when it is requested. The diagonal, coverage, and non-escape results \autoref{thm:cauchy-product-budgeted-bilinear-diagonal}, \autoref{thm:cauchy-product-shared-radius-product-coverage}, and \autoref{thm:cauchy-product-real-seal-multiplication-nonescape} identify the exact downstream boundary. Since all routes are already finite packet rows, no excluded analytic object can be handed to an L10 consumer.
\end{proof}

\begin{theorem}[CauchyProduct stream seal obligation]
\label{thm:cauchy-product-stream-seal-obligation}
Every $\CauchyProductUp$ root consumer that reads a product seal must first read the paired $\StreamNameUp$ windows
$$
W_X,W_Y
$$
together with the source-radius rows $M_X,M_Y$, the dyadic observation rows $Q_X,Q_Y$, the product row $P$, the $\RegSeqRatUp$ classifier row $E$, and the $\RealUp$ seal route. The obligation binds the stream windows to the regular-rational and real-seal reads through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it exports no host multiplication, quotient stream, selected limit, trichotomy row, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_stream\_seal\_obligation}
\begin{proof}
Begin with \autoref{thm:cauchy-product-root-source-admission}. It places the two $\RegularCauchyNameUp$ source rows, their $\StreamNameUp$ windows, and the $\DyadicRatCoreUp$ observations inside the same finite root surface.

Next apply \autoref{thm:cauchy-product-paired-window-regularity-exhaustion}. The theorem forces the product read through $W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N$ before any regular-rational or real-facing consumer can inspect the product.

Finally use the sibling seal boundaries from \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}. These chapters name the classifier and seal rows reached by the product packet, while \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-dyadicratcore-namecert} name the upstream finite-window and dyadic inputs. The displayed packet has no row for any excluded analytic object.
\end{proof}

\begin{theorem}[CauchyProduct real classifier obligation]
\label{thm:cauchy-product-real-classifier-obligation}
The product observation $P$ of an accepted $\CauchyProductUp$ packet reaches the real-facing classifier only through the displayed $\RegSeqRatUp$ classifier row $E$. The classifier route is determined by the paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, product-radius ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local naming row; it is not a host multiplication primitive, quotient-stream comparison, selected limit, trichotomy branch, independent real carrier, or ambient completeness statement.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_real\_classifier\_obligation}
\begin{proof}
Start with the product observation row $P$. By \autoref{thm:cauchy-product-root-classifier-stability}, transporting the paired source rows, windows, radius rows, dyadic observations, product observation, and classifier preserves the same finite root packet.

Now read the regular-rational classifier. The $\RegSeqRatUp$ boundary of \autoref{ch:concrete-instances-regseqrat-namecert} is reached only after the displayed window and dyadic rows have been consumed, and the radius conservation result \autoref{thm:cauchy-product-radius-budget-conservation} keeps the ledger attached to the same packet.

The real-facing read follows through the $\RealUp$ seal boundary, not through an external multiplication or completeness principle. Since the carrier exposes only the displayed classifier route, the excluded analytic objects cannot serve as alternative classifier evidence.
\end{proof}

\begin{theorem}[CauchyProduct ledger obligation]
\label{thm:cauchy-product-ledger-obligation}
The $\CauchyProductUp$ root ledger binds the radius rows, product row, transport rows, continuation rows, package provenance, and local NameCert row as one finite accounting surface:
$$
M_X,M_Y,Q_X,Q_Y,P,H,C,L,N.
$$
Every product-seal read must preserve this ledger when it passes to $\RegSeqRatUp$, $\RealUp$, $\RealAlgOrderUp$, or $\RealCompletenessUp$ consumers. The ledger contains no host multiplication estimate, quotient-stream equality, selected limit, trichotomy witness, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchy-product-radius-budget-conservation}. It identifies the input radii, dyadic product observations, product-radius witness, and classifier handoff as one conserved finite ledger.

Next combine the ledger with \autoref{thm:cauchy-product-shared-radius-product-coverage}. The multiplication-facing consumer can read the product only through the paired source windows, dyadic radius observations, budget rows, classifier row, real-seal handoff, and visible structural rows.

Finally route the same ledger to the completion side through \autoref{ch:concrete-instances-realcompleteness-namecert}. That chapter may consume the finite product-observation surface, while the ledger obligation keeps radius, product, transport, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed and leaves all excluded analytic objects outside the packet.
\end{proof}

\begin{theorem}[CauchyProduct downstream unblock]
\label{thm:cauchy-product-downstream-unblock}
Downstream $\RealAlgOrderUp$ and $\RealCompletenessUp$ consumers of an accepted $\CauchyProductUp$ packet receive only the finite product-observation surface
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
When an observation-budget packet is present, they may also read the displayed budget rows
$$
E_B,W_B,D_B,R_B,S_B,H_B,C_B,P_B,N_B.
$$
They receive no host multiplication, quotient stream, selected limit, trichotomy row, independent real carrier, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductUp.CauchyProductPacket\_downstream\_unblock}
\begin{proof}
Begin with \autoref{thm:cauchy-product-root-phase-handoff}. It states that every downstream L10 consumer factors through the paired windows, dyadic product route, radius ledger, regular-rational readback, real seal row, and local naming rows.

For the order-facing side, apply \autoref{thm:cauchy-product-shared-radius-product-coverage} and \autoref{thm:cauchy-product-real-seal-multiplication-nonescape}. The $\RealAlgOrderUp$ consumer sees a covered finite product observation, not a host multiplication primitive or quotient-stream comparison.

For the completion-facing side, read \autoref{ch:concrete-instances-realcompleteness-namecert} through the same product surface. The completion route may consume the finite product rows and, when present, the observation-budget rows named by \autoref{thm:cauchy-product-budgeted-readback-root-boundary}; it has no coordinate for selected limits, trichotomy, independent real carriers, or ambient completeness beyond the displayed packet.
\end{proof}

\begin{corollary}[CauchyProduct shared-window root strict local obstruction]
\label{cor:cauchy-product-shared-window-root-strict-obstruction}
Let $Z=(X,Y,W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N)$ be an accepted $\CauchyProductUp$ root formation packet. Suppose a displayed failure, refusal, separation, or countermodel row in the root-unblock obligations is cited against a named converse or reuse route for the shared-window root admission surface of \autoref{thm:cauchy-product-shared-window-root-admission}. Then the cited row is a strict local obstruction. It blocks only the named route whose consumer-facing read tries to omit, replace, detach, or bypass one of the displayed root coordinates
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N
$$
or one of the displayed support rows $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, together with any explicitly displayed $\RealObservationBudgetUp$ rows serving the same read. Every permitted consumer-facing use factors through those rows and rejects unlisted coordinates. The same cited row cannot be reinterpreted as a global impossibility statement for $\CauchyProductUp$, as a host theorem about multiplication or completion, as hidden external validation, as a quotient-stream argument, as a selected-limit argument, as a trichotomy row, as an independent real carrier, as an ambient completeness principle, or as an unbounded selector route.
\end{corollary}
\begin{proof}
First apply \autoref{thm:cauchy-product-shared-window-root-admission}. It admits a root-facing product route only through the paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ readback row, the $\RealUp$ seal, and the support rows $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Thus any consumer-facing use of a cited obstruction must first be located on the finite admitted root surface
$$
W_X,W_Y,M_X,M_Y,Q_X,Q_Y,P,E,H,C,L,N.
$$
In particular, a route that still factors through these displayed rows is not rejected by the corollary; only a named converse or reuse request that leaves the displayed surface has a challenged coordinate.

Next apply \autoref{thm:cauchyproduct-root-budget-nonescape}. It states that every exported product route is confined to paired finite windows, dyadic observations, product-observation rows, the $\RegSeqRatUp$ classifier, the $\RealUp$ seal, displayed transport, displayed continuation, package provenance, local naming, and any explicitly displayed $\RealObservationBudgetUp$ rows. It also excludes quotient streams, host real multiplication, ambient completeness, selected limits, trichotomy rows, independent real carriers, and unbounded selector rows from the exported root formation packet.

Now inspect the cited failure, refusal, separation, or countermodel row. If the named converse or reuse route tries to omit the paired windows, replace the dyadic observations, detach the product row from the classifier and seal, bypass $H,C,L,N$, or reuse the support rows away from $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, the cited row blocks exactly that local request. If the same row is read instead as a global impossibility, a host theorem, hidden external validation, a quotient-stream route, a selected-limit route, a trichotomy route, an independent real carrier, an ambient completeness principle, or an unbounded selector route, then \autoref{thm:cauchyproduct-root-budget-nonescape} supplies no coordinate through which that reading can be exported.

Therefore the obstruction has exactly the force of a strict local block against the named converse or reuse route. It factors every permitted consumer-facing use through the displayed shared-window root inventory and rejects every unlisted coordinate without asserting any global, host-level, or hidden validation claim.
\end{proof}
