\begin{theorem}[QuotientSoundnessBoundary consumer ledger coverage]
\label{thm:quotient-soundness-boundary-consumer-ledger-coverage}
Every downstream consumer read of an accepted
$\QuotientSoundnessBoundaryUp$ packet is covered by the finite ledger rows
$E,A,V,T,H,C,P,N$. The rows $A,V$ record the refused representative-style
request, while $E,T,H,C,P,N$ record the surviving classifier-respecting
$\psame$ transport route. The ledger exports no $\mathsf{Quot.sound}$ row and
no host quotient eliminator.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_consumer\_ledger\_coverage}
\begin{proof}
Read the negative coverage first. By
\autoref{thm:quotient-soundness-boundary-root-request-triad} and
\autoref{thm:quotient-soundness-boundary-root-relation-row-exposure}, each
root quotient-style request is visible through $E,A,V$.

Read the positive coverage next. The psame replacement classifier and root
transport package totality,
\autoref{thm:quotient-soundness-boundary-psame-replacement-classifier} and
\autoref{thm:quotient-soundness-boundary-root-transport-package-totality},
cover every surviving transport consumer by $E,T,H,C,P,N$.

It remains to exclude hidden exits. Apply
\autoref{thm:quotient-soundness-boundary-transport-refusal-normal-form},
\autoref{thm:quotient-soundness-boundary-kernel-nonescape}, and
\autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. The
combined ledger therefore covers downstream consumers without exporting
$\mathsf{Quot.sound}$ or a host quotient eliminator.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary downstream handoff readiness]
\label{thm:quotient-soundness-boundary-downstream-handoff-readiness}
The transport-refusal normal form and consumer ledger coverage assemble the
exact package that downstream quotient-like chapters may cite. That package is
the finite surface $E,A,V,T,H,C,P,N$ with refusal before transport,
classifier-respecting $\psame$ replacement, componentwise $\hsame$ stability,
displayed $\Cont$ locality, $\Pkg$ provenance, and local $\NameCert$ naming;
it contains no quotient primitive, no host quotient eliminator, no
representative-selection export, and no $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
First take the ordered refusal surface from
\autoref{thm:quotient-soundness-boundary-root-request-triad} and
\autoref{thm:quotient-soundness-boundary-root-transport-verdict-order}. These
rows make $A,V$ visible before any surviving transport handoff.

Next take the normal transport package from
\autoref{thm:quotient-soundness-boundary-transport-refusal-normal-form}. It
identifies the only surviving quotient-like operation as the displayed
$E,T,H,C,P,N$ route.

Now add ledger coverage by
\autoref{thm:quotient-soundness-boundary-consumer-ledger-coverage}. Every
downstream consumer read is therefore inside $E,A,V,T,H,C,P,N$.

Finally combine kernel non-escape with public bridge non-escape. The handoff
surface is ready for downstream citation precisely because no quotient
primitive, host quotient eliminator, representative-selection export, or
$\mathsf{Quot.sound}$ dependency crosses the package boundary.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary refusal transport sibling handoff]
\label{thm:quotient-soundness-boundary-refusal-transport-sibling-handoff}
Every downstream quotient-like sibling that consumes a
$\QuotientSoundnessBoundaryUp$ packet must read the representative-demand row
$A$ and refusal verdict row $V$ before reading the positive transport rows
$E,T,H,C,P,N$. The handoff supplies only classifier-respecting $\psame$
transport, componentwise $\hsame$ stability, displayed $\Cont$ locality,
$\Pkg$ provenance, and local $\NameCert$ naming over the finite $\BHist$
packet; it supplies no quotient carrier, host quotient eliminator,
representative-selection export, or $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
First read the refusal surface. The root request triad exposes the relation
rows $E$, representative-style demand rows $A$, and refusal verdict rows $V$,
while the verdict-order theorem places $V$ before any positive transport row is
available.

Next read the surviving transport surface. The transport-refusal normal form
and downstream handoff readiness identify the only exported positive route as
$E,T,H,C,P,N$, with $T$ carrying classifier-respecting $\psame$ transport and
$H,C,P,N$ carrying $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ structure.

Finally apply consumer ledger coverage and the public non-escape boundary. A
downstream sibling therefore receives refusal before transport and cannot cite
the packet as a source of $\mathsf{Quot.sound}$, quotient carriers, host
eliminators, or representative-selection exports.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary representative demand exposure]
\label{thm:quotient-soundness-boundary-representative-demand-exposure}
Under the sibling handoff of
\autoref{thm:quotient-soundness-boundary-refusal-transport-sibling-handoff},
the representative-demand rows $A$ remain audit-visible as part of the finite
$\BHist$ ledger. Later reads of $T,H,C,P,N$ may consume classifier-respecting
$\psame$ transport, componentwise $\hsame$ stability, displayed $\Cont$
locality, $\Pkg$ provenance, and local $\NameCert$ naming, but they cannot
erase $A$ or reread it as an admitted representative selector.
\end{theorem}
\begin{proof}
Begin with refusal locality. The representative-style demand is recorded in
$A$ together with the refusal verdict $V$ before the positive transport route
is available.

Now apply the sibling handoff. It carries $A,V$ forward as the visible negative
part of the surface and only then exposes the positive route through
$E,T,H,C,P,N$.

It remains to exclude erasure by later rows. Kernel non-escape and public
bridge non-escape remove the quotient-side coordinates, so $T,H,C,P,N$ have no
operation by which they can hide $A$, recover an erased representative demand,
or turn the refused demand into an admitted representative-selection export.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame consumer normalization]
\label{thm:quotient-soundness-boundary-psame-consumer-normalization}
Every surviving quotient-like consumer route of an accepted
$\QuotientSoundnessBoundaryUp$ packet normalizes, after the refusal rows
$A,V$ have been read, to the displayed transport surface $E,T,H,C,P,N$. The
normal form is a $\psame$ consumer route with componentwise $\hsame$ stability,
displayed $\Cont$ locality, $\Pkg$ provenance, and local $\NameCert$ naming; it
has no quotient carrier coordinate and no host eliminator coordinate.
\end{theorem}
\begin{proof}
Read the classifier first. The $\psame$ replacement classifier identifies the
positive consumer operation as the displayed transport row $T$ over the named
relation rows $E$.

Then use consumer ledger coverage. Once refusal has been recorded in $A,V$,
every surviving consumer read is covered by the positive rows $E,T,H,C,P,N$
and by no additional quotient-side row.

Finally apply the sibling handoff together with kernel non-escape. The
surviving consumer route therefore normalizes to the displayed $\psame$
transport route and cannot pass through a quotient carrier, a host quotient
eliminator, or a hidden $\mathsf{Quot.sound}$ dependency.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary refusal verdict monotonicity]
\label{thm:quotient-soundness-boundary-refusal-verdict-monotonicity}
In an accepted $\QuotientSoundnessBoundaryUp$ packet, adding later transport rows cannot turn a refused representative-selection row $A,V$ into an admitted quotient primitive. The rows $E,T,H,C,P,N$ may supply the classifier-respecting $\psame$ replacement route after refusal, but they cannot reread $A,V$ as a representative selector, quotient equality eliminator, host quotient eliminator, unrestricted quotient recursion principle, or $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
Start with the negative row. The root request triad, \autoref{thm:quotient-soundness-boundary-root-request-triad}, records representative-selection demand in $A$ and refusal in $V$ before transport is available.

The order statement \autoref{thm:quotient-soundness-boundary-root-transport-verdict-order} separates verdict from transport. Thus later use of $T$ is downstream of the refused request rather than a replacement for the refusal verdict.

Use \autoref{thm:quotient-soundness-boundary-psame-replacement-classifier} for the positive route. It gives only classifier-respecting $\psame$ transport through $E,T,H,C,P,N$.

Finally apply \autoref{thm:quotient-soundness-boundary-non-escape} and \autoref{thm:quotient-soundness-boundary-kernel-refusal-ledger}. The packet has no coordinate by which later transport rows can promote a refused representative request into an admitted quotient primitive.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary downstream factorization exactness]
\label{thm:quotient-soundness-boundary-downstream-factorization-exactness}
Every downstream quotient-like consumer of $\QuotientSoundnessBoundaryUp$ factors through exactly one of the two displayed surfaces: either the refused request pair $A,V$ or the $\psame$ transport package $E,T,H,C,P,N$. There is no third route through a quotient carrier, representative selector, quotient equality eliminator, erased derivation recovery map, host-level class selector, unrestricted quotient recursion principle, or $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
Read the negative surface first. By \autoref{thm:quotient-soundness-boundary-root-request-triad}, \autoref{thm:quotient-soundness-boundary-root-relation-row-exposure}, and \autoref{thm:quotient-soundness-boundary-root-transport-verdict-order}, a representative-style request must expose $E$, then read $A,V$, before any surviving transport can be used.

Read the positive surface next. By \autoref{thm:quotient-soundness-boundary-psame-replacement-classifier} and \autoref{thm:quotient-soundness-boundary-root-transport-package-totality}, every surviving classifier-respecting consumer route is packaged by $E,T,H,C,P,N$.

The classifier boundary is exact because \autoref{thm:quotient-soundness-boundary-non-escape} removes the quotient-side primitives, while \autoref{thm:quotient-soundness-boundary-kernel-refusal-ledger} records the exported surface as refusal plus displayed transport.

Finally apply \autoref{thm:quotient-soundness-boundary-psame-replacement-classifier} again to identify the positive side as the named $\psame$ replacement rather than a hidden quotient route. The downstream consumer therefore has only the refused pair or the displayed transport package.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary kernel refusal ledger]
\label{thm:quotient-soundness-boundary-kernel-refusal-ledger}
The root request triad, the $\psame$ replacement classifier, and kernel non-escape assemble the kernel-facing refusal ledger consumed by downstream quotient-like chapters. The exported surface consists of the refused request rows $E,A,V$ together with the classifier-respecting transport rows $E,T,H,C,P,N$, and no $\mathsf{Quot.sound}$ or host quotient eliminator enters that surface.
\end{theorem}
\begin{proof}
Use \autoref{thm:quotient-soundness-boundary-root-request-triad} for the negative part of the ledger. It binds each root quotient-style request to the visible relation evidence $E$, the requested representative rows $A$, and the refusal verdict $V$.

Use \autoref{thm:quotient-soundness-boundary-psame-replacement-classifier} for the positive replacement route. It identifies the accepted classifier-respecting consumer path as $E,T,H,C,P,N$, with $T$ carrying the displayed $\psame$ transport.

Finally apply \autoref{thm:quotient-soundness-boundary-kernel-nonescape}. The kernel-facing packet cannot project $\mathsf{Quot.sound}$, a host quotient eliminator, a hidden representative selector, or erased relation-derivation recovery, so downstream quotient-like chapters receive refusal plus displayed transport rather than a hidden quotient principle.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary NameCert ledger]
\label{thm:quotient-soundness-boundary-namecert-ledger}
The carrier of \autoref{def:quotient-soundness-boundary-carrier}, the fixed classifier of \autoref{thm:quotient-soundness-boundary-fixed-classifier}, the transport replacement of \autoref{thm:quotient-soundness-boundary-transport-replacement}, the negative-refusal dependency of \autoref{thm:quotient-soundness-boundary-negative-refusal-dependency}, and the kernel non-escape theorem of \autoref{thm:quotient-soundness-boundary-kernel-nonescape} assemble the local $\NameCert_{\QuotientSoundnessBoundaryUp}$ ledger.
\end{theorem}
\begin{proof}
The carrier supplies the finite inventory $E,A,T,V,H,C,P,N$. The fixed classifier theorem binds every accepted comparison to the displayed relation, request, replacement, verdict, and transport rows.

The transport replacement theorem supplies the positive operation available to downstream consumers. It routes classifier-respecting reads through named source rows rather than through selected quotient representatives.

The negative-refusal dependency and kernel non-escape theorems complete the ledger. They record the blocked quotient-soundness demand as a negative boundary request and keep every exported consumer inside $E,A,T,V,H,C,P,N$, so the local naming certificate contains exactly the quotient-boundary obligations listed in \autoref{thm:quotient-soundness-boundary-namecert-obligations}.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary public bridge]
\label{thm:quotient-soundness-boundary-public-bridge}
Every downstream quotient-like consumer of an accepted $\QuotientSoundnessBoundaryUp$ packet must read the public boundary through the finite rows
$$
E,A,T,V,H,C,P,N.
$$
The fixed classifier, transport replacement, negative-refusal dependency, kernel non-escape theorem, and NameCert ledger make this the whole public bridge: it admits relation rows, requested-representative refusal, classifier-respecting $\psame$ transport, componentwise stability, continuation, provenance, and local naming, but it excludes quotient carriers, representative selectors, quotient equality eliminators, erased derivation recovery, and $\mathsf{Quot.sound}$.
\end{theorem}
\begin{proof}
Project the carrier and apply the fixed classifier theorem. Every accepted comparison is already read through $E,A,T,V,H,C$, so no downstream consumer can widen the comparison by consulting a quotient carrier or representative selector.

Use transport replacement for the positive route. It routes quotient-like use through the source relation rows $E$, the classifier-respecting transport row $T$, and the structural rows $H,C,P,N$.

Use the negative-refusal dependency for blocked representative requests. The rows $A,V$ record those requests as refused boundary reads before any surviving transport is consumed.

Finally apply kernel non-escape and the NameCert ledger. Kernel non-escape removes quotient equality eliminators, erased derivation recovery, and $\mathsf{Quot.sound}$ from the exported packet, while the ledger assembles the remaining rows as the finite public boundary.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary bridge schema]
\label{thm:quotient-soundness-boundary-bridge-schema}
Every accepted $\QuotientSoundnessBoundaryUp$ carrier presents a bridge from the finite refusal-and-transport packet to the public quotient-refusal schema. The bridge reads the relation rows $E$, requested representative rows $A$, classifier-respecting $\psame$ transport row $T$, refusal verdict $V$, componentwise $\hsame$ transport row $H$, continuation rows $C$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $N$, and it imports no $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:quotient-soundness-boundary-carrier}. Its public quotient-facing surface is already the finite tuple $E,A,T,V,H,C,P,N$.

Use the NameCert ledger, \autoref{thm:quotient-soundness-boundary-namecert-ledger}, to assemble the refusal row $A,V$ and the transport route $E,T,H,C,P,N$ as one public packet. The fixed classifier theorem keeps comparison reads inside the same rows.

Finally apply non-escape, \autoref{thm:quotient-soundness-boundary-non-escape}. Since the excluded quotient primitives and $\mathsf{Quot.sound}$ have no coordinate in the carrier, the bridge is exactly the displayed refusal-and-transport schema.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame bridge handoff]
\label{thm:quotient-soundness-boundary-psame-bridge-handoff}
After the public refusal row $A,V$ has been read, the only bridge handoff available to a quotient-like consumer is the classifier-respecting $\psame$ route $E,T,H,C,P,N$. The handoff supplies named-source transport and does not supply a representative selector, quotient equality eliminator, erased derivation recovery map, or $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
Start with the refusal-locality theorem, \autoref{thm:quotient-soundness-boundary-refusal-locality}. It places every representative-selection demand in $A,V$ before the positive transport route is consumed.

Then use $\psame$ transport exhaustion, \autoref{thm:quotient-soundness-boundary-psame-transport-exhaustion}. The surviving operation is exhausted by $E,T,H,C,P,N$, with $T$ carrying classifier-respecting transport on named source rows.

The non-escape theorem removes the quotient-side objects from the handoff. Thus the bridge gives downstream consumers a displayed $\psame$ route and no quotient-soundness primitive.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary refusal-transport determinacy]
\label{thm:quotient-soundness-boundary-refusal-transport-determinacy}
For every accepted $\QuotientSoundnessBoundaryUp$ packet
$$
Q=(E,A,T,V,H,C,P,N),
$$
once the representative request recorded in $A$ has been refused by $V$, any accepted quotient-like consumer route is determined by the displayed $\psame$ route through $E,T,H,C,P,N$. The consumer cannot choose a second route through a quotient carrier, representative selector, quotient equality eliminator, erased derivation recovery map, host-level class selector, unrestricted quotient recursion principle, or $\mathsf{Quot.sound}$ dependency.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:quotient-soundness-boundary-carrier}. Its rows display the relation evidence $E$, representative requests $A$, $\psame$ transport $T$, refusal verdict $V$, componentwise stability $H$, continuation routes $C$, provenance $P$, and local naming $N$.

Use refusal locality, \autoref{thm:quotient-soundness-boundary-refusal-locality}. It forces the representative-selection demand to be read as the local pair $A,V$ before any positive transport is consumed.

After that refusal, apply $\psame$ transport exhaustion, \autoref{thm:quotient-soundness-boundary-psame-transport-exhaustion}, together with the bridge handoff, \autoref{thm:quotient-soundness-boundary-psame-bridge-handoff}. These results identify $E,T,H,C,P,N$ as the displayed consumer route after refusal.

Finally use kernel non-escape, \autoref{thm:quotient-soundness-boundary-kernel-nonescape}, and the public bridge, \autoref{thm:quotient-soundness-boundary-public-bridge}. Since the excluded quotient primitives have no coordinate in the packet, the accepted consumer has no second quotient route to select.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary source-row consumer totality]
\label{thm:quotient-soundness-boundary-source-row-consumer-totality}
Every surviving quotient-like consumer of an accepted $\QuotientSoundnessBoundaryUp$ packet must expose the source relation rows $E$ before it reads the positive transport row $T$. All consumer-facing data in the packet is exhausted by the finite rows
$$
E,A,T,V,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:quotient-soundness-boundary-carrier}. The row $E$ is the source relation surface, while $T$ is the classifier-respecting $\psame$ transport replacement available only as part of the displayed packet.

Apply root relation row exposure, \autoref{thm:quotient-soundness-boundary-root-relation-row-exposure}, and root transport verdict order, \autoref{thm:quotient-soundness-boundary-root-transport-verdict-order}. These force relation exposure and refusal to be visible before the positive transport row can be consumed.

Then use $\psame$ transport exhaustion and the bridge handoff. The surviving consumer route is the single path through $E,T,H,C,P,N$ after the refusal pair $A,V$ has been read.

Kernel non-escape and the public bridge complete the totality claim. They keep every consumer-facing read inside $E,A,T,V,H,C,P,N$ and exclude quotient carriers, hidden representative selectors, erased derivation recovery, host quotient eliminators, and $\mathsf{Quot.sound}$.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary verdict-transport separation]
\label{thm:quotient-soundness-boundary-verdict-transport-separation}
In every accepted $\QuotientSoundnessBoundaryUp$ packet $Q=(E,A,T,V,H,C,P,N)$, the row $V$ is a negative refusal row for the representative request in $A$, while $T$ is a positive classifier-respecting $\psame$ transport row on the source relation surface $E$. Neither row can be reread as the other, and neither row can be reread as $\mathsf{Quot.sound}$.
\end{theorem}
\begin{proof}
The carrier separates the roles at the level of rows. The row $V$ records the refusal verdict for the requested representative surface in $A$, while $T$ records the positive $\psame$ transport replacement over the relation rows $E$.

Use refusal locality to read $A,V$ as the negative part of the packet before transport. Use $\psame$ transport exhaustion and the bridge handoff to read $E,T,H,C,P,N$ as the positive route made available after that refusal.

The two readings therefore have different positions and different consumer roles inside the finite packet. The verdict row blocks representative selection; the transport row carries classifier-respecting named-source transport.

Finally apply kernel non-escape and the public bridge non-escape, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. Since $\mathsf{Quot.sound}$ and the host quotient primitives are outside the public bridge, neither $V$ nor $T$ can be reinterpreted as a quotient-soundness primitive.
\end{proof}
