\begin{theorem}[QuotientSoundnessBoundary public bridge non-escape]
\label{thm:quotient-soundness-boundary-public-bridge-nonescape}
The public bridge supplied by $\QuotientSoundnessBoundaryUp$ is non-escaping: every consumer read remains inside $E,A,T,V,H,C,P,N$, and any request for quotient carriers, representative selectors, quotient equality eliminators, erased derivation recovery maps, host-level class selectors, unrestricted quotient recursion, or $\mathsf{Quot.sound}$ lies outside the bridge.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_public\_bridge\_nonescape}
\begin{proof}
Apply the bridge schema theorem above to identify the public bridge with the refusal-and-transport tuple $E,A,T,V,H,C,P,N$.

Apply the $\psame$ bridge handoff theorem above for the positive route after refusal. It leaves only named-source transport through $E,T,H,C,P,N$.

Finally apply \autoref{thm:quotient-soundness-boundary-kernel-nonescape}. The kernel-facing route has no quotient primitive coordinate, so any request for such an object must be supplied by a separate certificate outside this chapter.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary erased derivation refusal]
\label{thm:quotient-soundness-boundary-erased-derivation-refusal}
For every accepted $\QuotientSoundnessBoundaryUp$ packet
$$
Q=(E,A,T,V,H,C,P,N),
$$
any request to recover an erased quotient derivation is first routed to the representative-request row $A$ and the refusal-verdict row $V$. The request is refused before the positive transport row $T$ is readable by a downstream consumer.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_erased\_derivation\_refusal\_certificate}
\begin{proof}
The carrier in \autoref{def:quotient-soundness-boundary-carrier} separates representative requests, refusal verdicts, and positive transport into the rows $A,V,T$. A recovery demand for an erased derivation is therefore not a transport demand; it is a representative-side demand.

Apply refusal locality, \autoref{thm:quotient-soundness-boundary-refusal-locality}. It forces the demand through $A,V$ before any consumer can use the positive transport route.

Then use verdict-transport separation, \autoref{thm:quotient-soundness-boundary-verdict-transport-separation}. The refusal row $V$ cannot be reread as the transport row $T$, and $T$ cannot be used to reconstruct a denied representative witness.

Finally apply public bridge non-escape, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. Erased derivation recovery has no bridge coordinate, so the only public response is the local refusal recorded by $A,V$.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame-only descent]
\label{thm:quotient-soundness-boundary-psame-only-descent}
After the refusal of representative recovery in an accepted $\QuotientSoundnessBoundaryUp$ packet $Q=(E,A,T,V,H,C,P,N)$, every accepted descent route factors only through $E,T,H,C,P,N$ using classifier-respecting $\psame$ transport. No accepted descent route uses representative selection, quotient equality elimination, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{theorem}
\begin{proof}
Begin after the refusal supplied by \autoref{thm:quotient-soundness-boundary-erased-derivation-refusal}. At that point the consumer may read the positive route only as a route downstream of $A,V$.

Apply $\psame$ transport exhaustion, \autoref{thm:quotient-soundness-boundary-psame-transport-exhaustion}. It identifies the surviving positive descent as classifier-respecting $\psame$ transport through $E,T,H,C,P,N$.

Use the $\psame$ bridge handoff, \autoref{thm:quotient-soundness-boundary-psame-bridge-handoff}, to pass this displayed route to the public bridge. Then apply source-row consumer totality, \autoref{thm:quotient-soundness-boundary-source-row-consumer-totality}, which exhausts the downstream read by the finite rows $E,A,T,V,H,C,P,N$.

The excluded quotient primitives have no coordinate in those rows. Hence an accepted descent route is psame-only and cannot pass through representative selection, quotient equality elimination, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{proof}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_psame\_only\_descent}

\begin{theorem}[QuotientSoundnessBoundary consumer non-escape]
\label{thm:quotient-soundness-boundary-consumer-nonescape}
Every downstream quotient-like consumer of an accepted $\QuotientSoundnessBoundaryUp$ packet is exhausted by the finite rows
$$
E,A,T,V,H,C,P,N.
$$
It cannot reinterpret the refusal verdict $V$ or the positive transport row $T$ as quotient equality elimination, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{theorem}
\begin{proof}
First apply erased derivation refusal, \autoref{thm:quotient-soundness-boundary-erased-derivation-refusal}. Any recovery demand is already localized to $A,V$ and refused before $T$ is available.

Next apply psame-only descent, \autoref{thm:quotient-soundness-boundary-psame-only-descent}. The surviving positive route factors through $E,T,H,C,P,N$ as classifier-respecting $\psame$ transport.

Finally use public bridge non-escape, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. Since every consumer read stays inside $E,A,T,V,H,C,P,N$, neither $V$ nor $T$ can be reinterpreted as a quotient-side eliminator, recovery map, recursion principle, or $\mathsf{Quot.sound}$ witness.
\end{proof}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_consumer\_nonescape}

\begin{theorem}[QuotientSoundnessBoundary representative request frontier]
\label{thm:quotient-soundness-boundary-representative-request-frontier}
For every accepted $\QuotientSoundnessBoundaryUp$ packet $Q=(E,A,T,V,H,C,P,N)$, any request for a representative, representative selector, erased derivation, or host quotient witness is exhausted by the source row $E$, representative-request row $A$, and refusal-verdict row $V$ before the positive transport row $T$ is readable. The request therefore reaches a visible refusal frontier before any downstream $\psame$ transport is exposed.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_representative\_request\_frontier}
\begin{proof}
Start with erased derivation refusal, \autoref{thm:quotient-soundness-boundary-erased-derivation-refusal}. It routes recovery demands to $A,V$ before the positive transport row is available.

Apply refusal locality and verdict-transport separation, \autoref{thm:quotient-soundness-boundary-refusal-locality} and \autoref{thm:quotient-soundness-boundary-verdict-transport-separation}. These rows prevent a representative request from being reread as transport and prevent $T$ from reconstructing a denied witness.

Finally use consumer non-escape, \autoref{thm:quotient-soundness-boundary-consumer-nonescape}. The public consumer remains inside $E,A,T,V,H,C,P,N$, so the representative-side request is exhausted at $E,A,V$ before transport can be used.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame consumer closure]
\label{thm:quotient-soundness-boundary-psame-consumer-closure}
After the representative frontier refuses the representative-side request, every surviving downstream consumer closes through $E,T,H,C,P,N$ by classifier-respecting $\psame$ transport. The surviving route has no representative selector, quotient equality eliminator, erased derivation recovery map, host quotient recursion, or $\mathsf{Quot.sound}$ coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_psame\_consumer\_closure}
\begin{proof}
First apply the representative request frontier above. It leaves the positive route available only after $E,A,V$ have already recorded the refusal boundary.

Use psame-only descent, \autoref{thm:quotient-soundness-boundary-psame-only-descent}. The surviving route factors through $E,T,H,C,P,N$ as classifier-respecting $\psame$ transport.

Then apply the public bridge non-escape theorem, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. The bridge has no coordinate for the excluded quotient primitives, so the psame-only consumer route is closed by the displayed finite rows.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary Quot.sound refusal exactness]
\label{thm:quotient-soundness-boundary-quot-sound-refusal-exactness}
In an accepted $\QuotientSoundnessBoundaryUp$ packet, a request for $\mathsf{Quot.sound}$ is refused exactly at the visible boundary rows $E,A,V$ and cannot be served by the positive transport row $T$ or by the consumer rows $H,C,P,N$. Conversely, the admitted positive route through $E,T,H,C,P,N$ is precisely the $\psame$-only route that remains after that refusal.
\end{theorem}
\begin{proof}
For the refusal direction, apply the representative request frontier above. A $\mathsf{Quot.sound}$ demand is a representative-side quotient primitive request, so it is routed to $E,A,V$ before $T$ is readable.

Apply kernel non-escape and public bridge non-escape, \autoref{thm:quotient-soundness-boundary-kernel-nonescape} and \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. Neither the kernel-facing route nor the bridge exposes a $\mathsf{Quot.sound}$ coordinate.

For the surviving route, use psame consumer closure above. Once the refusal is recorded, every admitted consumer is exactly the classifier-respecting $\psame$ route through $E,T,H,C,P,N$, so the refusal boundary and the positive route are exact complements inside the finite packet.
\end{proof}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_quot\_sound\_refusal\_exactness}

\begin{theorem}[QuotientSoundnessBoundary refusal stability row]
\label{thm:quotient-soundness-boundary-refusal-stability-row}
In every accepted $\QuotientSoundnessBoundaryUp$ packet $Q=(E,A,T,V,H,C,P,N)$, componentwise $\hsame$ transport through the history row $H$ preserves the visible refusal pair $A,V$ and the surviving transport row $T$. The stable row remains a refusal-and-$\psame$ ledger entry and does not admit representative selection, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_refusal\_stability\_row}
\begin{proof}
The carrier definition, \autoref{def:quotient-soundness-boundary-carrier}, makes $H$ a row of the finite packet rather than a quotient eliminator. Hence componentwise $\hsame$ transport can only move along the displayed history coordinate of $Q$.

Apply the representative request frontier, \autoref{thm:quotient-soundness-boundary-representative-request-frontier}. It fixes the visible refusal boundary at $E,A,V$ before the positive transport row $T$ is available.

Then apply psame consumer closure, \autoref{thm:quotient-soundness-boundary-psame-consumer-closure}. After the refusal boundary is recorded, the surviving consumer route is exactly the classifier-respecting $\psame$ route through $E,T,H,C,P,N$.

Finally use Quot.sound refusal exactness, \autoref{thm:quotient-soundness-boundary-quot-sound-refusal-exactness}. Since $\mathsf{Quot.sound}$ is refused at $E,A,V$ and the admitted route is the displayed $\psame$ route, $\hsame$ transport through $H$ cannot create a hidden representative selector or quotient-soundness witness.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary Cont route locality]
\label{thm:quotient-soundness-boundary-cont-route-locality}
Every consumer route through the continuation row $C$ of an accepted $\QuotientSoundnessBoundaryUp$ packet reads the relation rows $E$, then the refusal rows $A,V$, and then the positive $\psame$ transport row $T$ in the displayed order. There is no hidden route through a quotient eliminator, representative selector, erased derivation recovery map, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_cont\_route\_locality}
\begin{proof}
The carrier definition places $C$ after the source, refusal, transport, and history rows in the finite packet $Q=(E,A,T,V,H,C,P,N)$. A continuation consumer therefore receives only the rows already exposed by the packet.

Use the representative request frontier, \autoref{thm:quotient-soundness-boundary-representative-request-frontier}, to locate every representative-side demand at $E,A,V$ before any positive transport is readable.

Next apply psame consumer closure, \autoref{thm:quotient-soundness-boundary-psame-consumer-closure}. It identifies the route available to $C$ as the classifier-respecting $\psame$ route through $E,T,H,C,P,N$ after the refusal frontier has been crossed.

Quot.sound refusal exactness, \autoref{thm:quotient-soundness-boundary-quot-sound-refusal-exactness}, rules out the hidden branch. The continuation row has no coordinate that can bypass $A,V$ or reinterpret $T$ as $\mathsf{Quot.sound}$.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary Pkg NameCert ledger totality]
\label{thm:quotient-soundness-boundary-pkg-namecert-ledger-totality}
In every accepted $\QuotientSoundnessBoundaryUp$ packet, the package row $P$ and NameCert row $N$ account for the whole finite ledger $E,A,T,V,H,C$. The exported object is exactly this ledger package and exports no quotient carrier, representative selector, quotient equality eliminator, erased derivation recovery primitive, host quotient recursion principle, or $\mathsf{Quot.sound}$ primitive.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_pkg\_namecert\_ledger\_totality}
\begin{proof}
By the carrier definition, the public packet has exactly the displayed rows $Q=(E,A,T,V,H,C,P,N)$. The rows $P,N$ package and certify the preceding ledger rows; they are not extra quotient primitives.

Apply the representative request frontier to account for the refusal ledger $E,A,V$. It records every representative-side request before positive transport is exposed.

Apply psame consumer closure to account for the positive ledger $E,T,H,C,P,N$. The downstream route that survives the refusal is the classifier-respecting $\psame$ route over the displayed packet.

Finally use Quot.sound refusal exactness. Since $\mathsf{Quot.sound}$ is refused exactly at the visible boundary and the surviving route is already exhausted by the packet rows, $P,N$ are total for the finite ledger and cannot export any additional quotient primitive.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame request determinacy]
\label{thm:quotient-soundness-boundary-psame-request-determinacy}
For every accepted $\QuotientSoundnessBoundaryUp$ packet $Q=(E,A,T,V,H,C,P,N)$, a representative-side request is deterministically routed to the visible refusal rows $E,A,V$ before the admitted $\psame$ route through $E,T,H,C,P,N$ is readable. Thus a downstream consumer can read either the recorded refusal frontier or the surviving classifier-respecting $\psame$ transport, but it receives no ambiguous branch between representative access and positive transport.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_psame\_request\_determinacy}
\begin{proof}
Apply the representative request frontier, \autoref{thm:quotient-soundness-boundary-representative-request-frontier}. It sends every representative, selector, erased-derivation, host-quotient, and $\mathsf{Quot.sound}$ demand to $E,A,V$ before $T$ is exposed.

Next use psame consumer closure, \autoref{thm:quotient-soundness-boundary-psame-consumer-closure}. After the refusal frontier is recorded, the only surviving positive consumer is the classifier-respecting $\psame$ route through $E,T,H,C,P,N$.

The two surfaces are separated by Quot.sound refusal exactness, \autoref{thm:quotient-soundness-boundary-quot-sound-refusal-exactness}. Hence the packet presents a determined refusal surface first and a determined $\psame$ surface second, with no hidden branch that can choose a representative route.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary NameCert refusal totality]
\label{thm:quotient-soundness-boundary-namecert-refusal-totality}
For every accepted $\QuotientSoundnessBoundaryUp$ packet, the package row $P$ and NameCert row $N$ are total for the refusal-plus-transport ledger consisting of the visible refusal rows $E,A,V$ and the admitted transport rows $E,T,H,C,P,N$. The certified export exposes no $\mathsf{Quot.sound}$ primitive, representative selector, erased-derivation recovery coordinate, or host quotient recursion coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_namecert\_refusal\_totality}
\begin{proof}
First apply psame request determinacy above. It fixes the order in which $E,A,V$ are readable as refusal rows and $E,T,H,C,P,N$ are readable as the positive $\psame$ route.

Use Cont route locality, \autoref{thm:quotient-soundness-boundary-cont-route-locality}, to keep continuation consumers inside that displayed route. The continuation row cannot bypass $A,V$ or reinterpret $T$ as a quotient eliminator.

Finally apply Pkg NameCert ledger totality, \autoref{thm:quotient-soundness-boundary-pkg-namecert-ledger-totality}. Since $P,N$ already certify the entire finite ledger and expose no excluded quotient primitive, the NameCert surface is total for exactly the refusal-plus-transport ledger stated here.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary downstream representative non-escape]
\label{thm:quotient-soundness-boundary-downstream-representative-nonescape}
Every downstream consumer of the $\QuotientSoundnessBoundaryUp$ chapter factors through the deterministic refusal surface of \autoref{thm:quotient-soundness-boundary-psame-request-determinacy} and the total NameCert surface of \autoref{thm:quotient-soundness-boundary-namecert-refusal-totality}. Consequently the surviving $\psame$ route through $E,T,H,C,P,N$ cannot be reinterpreted as a quotient eliminator, representative selector, erased-derivation recovery map, host quotient recursion principle, or $\mathsf{Quot.sound}$ witness.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_downstream\_representative\_nonescape\_certificate}
\begin{proof}
Apply psame request determinacy to determine the public request boundary. A downstream consumer first sees the visible refusal rows $E,A,V$ and only then the classifier-respecting $\psame$ route through $E,T,H,C,P,N$.

Apply NameCert refusal totality above. The certified export is the finite refusal-plus-transport ledger, so its public rows expose no representative selector, recovery coordinate, host quotient recursion coordinate, or $\mathsf{Quot.sound}$ primitive.

Use Cont route locality and Pkg NameCert ledger totality, \autoref{thm:quotient-soundness-boundary-cont-route-locality} and \autoref{thm:quotient-soundness-boundary-pkg-namecert-ledger-totality}. They force every continuation and package read to stay inside the same finite ledger, so the surviving $\psame$ route is a consumer closure route rather than a quotient eliminator.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary refusal exact complement]
\label{thm:quotient-soundness-boundary-refusal-exact-complement}
In an accepted $\QuotientSoundnessBoundaryUp$ packet
$$
Q=(E,A,T,V,H,C,P,N),
$$
every downstream consumer request is either the visible representative-side refusal through $E,A,V$ or the admitted $\psame$-only route through $E,T,H,C,P,N$. These two surfaces are exact complements inside the finite packet: a request that asks for a representative, selector, erased-derivation recovery, host quotient recursion, quotient equality eliminator, or $\mathsf{Quot.sound}$ witness is refused at $E,A,V$, while a request that survives the refusal boundary factors through the classifier-respecting $\psame$ route and no third route remains.
\end{theorem}
\begin{proof}
Apply the representative request frontier, \autoref{thm:quotient-soundness-boundary-representative-request-frontier}. It places every representative-side demand at the visible refusal surface $E,A,V$ before a positive transport row can be consumed.

Use psame consumer closure, \autoref{thm:quotient-soundness-boundary-psame-consumer-closure}. Once the representative-side request has been refused, the surviving consumer route is the classifier-respecting $\psame$ route through $E,T,H,C,P,N$.

Invoke Quot.sound refusal exactness, \autoref{thm:quotient-soundness-boundary-quot-sound-refusal-exactness}. It separates the forbidden representative primitive from the admitted $\psame$ transport, so the refusal surface cannot be reinterpreted as a hidden quotient witness.

Finally apply NameCert refusal totality, \autoref{thm:quotient-soundness-boundary-namecert-refusal-totality}. The package and naming rows certify only the refusal-plus-transport ledger, hence the two surfaces exhaust the finite packet and form exact complements for downstream consumers.
\end{proof}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_refusal\_exact\_complement\_certificate}

\begin{theorem}[QuotientSoundnessBoundary consumer scope triad]
\label{thm:quotient-soundness-boundary-consumer-scope-triad}
Every downstream quotient-like consumer of an accepted $\QuotientSoundnessBoundaryUp$ packet must first read the refusal surface $E,A,V$: the visible relation rows $E$, the representative-demand rows $A$, and the refusal verdict rows $V$. Only after that triad is visible may the consumer read any positive motion through the classifier-respecting $\psame$ route $E,T,H,C,P,N$. The handoff receives no quotient carrier, representative selector, erased derivation recovery map, host quotient recursion principle, or $\mathsf{Quot.sound}$ witness.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_consumer\_scope\_triad\_certificate}
\begin{proof}
Use psame request determinacy, \autoref{thm:quotient-soundness-boundary-psame-request-determinacy}. It routes every representative-side request to $E,A,V$ before the positive $\psame$ route is readable.

Apply NameCert refusal totality, \autoref{thm:quotient-soundness-boundary-namecert-refusal-totality}. The certified export is the finite refusal-plus-transport ledger, so a downstream consumer reads the refusal triad before it receives the transport rows.

Finally use downstream representative non-escape above. It keeps the surviving route inside $E,T,H,C,P,N$ and excludes quotient carriers, representative selectors, erased derivation recovery, host quotient recursion, and $\mathsf{Quot.sound}$ from the handoff.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary psame consumer factorization]
\label{thm:quotient-soundness-boundary-psame-consumer-factorization}
After the refusal surface $E,A,V$ has been read, every surviving positive motion of a downstream quotient-like consumer factors only through the classifier-respecting $\psame$ package $E,T,H,C,P,N$. The factorization uses the displayed relation rows, transport replacement, componentwise $\hsame$ stability, $\Cont$ locality, $\Pkg$ provenance, and local $\NameCert$ naming, and it has no coordinate for a quotient carrier, representative selector, erased derivation recovery map, host quotient recursion principle, or $\mathsf{Quot.sound}$ witness.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_psame\_consumer\_factorization}
\begin{proof}
Begin with the consumer scope triad above. It places the downstream read at $E,A,V$ before any positive transport row can be consumed.

Use psame consumer closure, \autoref{thm:quotient-soundness-boundary-psame-consumer-closure}. Once the representative-side request is refused, every accepted consumer closes through the classifier-respecting route $E,T,H,C,P,N$.

Use Pkg NameCert ledger totality, \autoref{thm:quotient-soundness-boundary-pkg-namecert-ledger-totality}, to account for the package and naming rows in the same factorization.

Finally apply public bridge non-escape, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. The bridge exports no quotient carrier, representative selector, recovery coordinate, host quotient recursion, or $\mathsf{Quot.sound}$ witness, so the displayed $\psame$ package is the only surviving route.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary downstream boundary readiness]
\label{thm:quotient-soundness-boundary-downstream-boundary-readiness}
The consumer scope triad and psame consumer factorization assemble the downstream boundary package for $\QuotientSoundnessBoundaryUp$. A downstream quotient-like chapter receives the refusal surface $E,A,V$ first and then, for any surviving positive motion, the classifier-respecting $\psame$ route $E,T,H,C,P,N$; it receives no quotient carrier, representative selector, erased derivation recovery map, host quotient recursion principle, or $\mathsf{Quot.sound}$ witness.
\end{theorem}
\begin{proof}
First apply the consumer scope triad. It fixes the downstream entry surface as $E,A,V$, with visible relation rows, requested representative rows, and refusal verdict rows read before positive transport.

Next apply psame consumer factorization above. It identifies every surviving positive motion with the displayed classifier-respecting route $E,T,H,C,P,N$.

Finally use downstream representative non-escape together with public bridge non-escape. These results prevent the boundary package from exporting quotient carriers, representative selectors, erased derivation recovery maps, host quotient recursion, or $\mathsf{Quot.sound}$ witnesses, so the chapter is ready as a downstream nonimport boundary.
\end{proof}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_downstream\_boundary\_readiness}

\begin{theorem}[QuotientSoundnessBoundary downstream nonimport totality]
\label{thm:quotient-soundness-boundary-downstream-nonimport-totality}
Every downstream consumer of an accepted $\QuotientSoundnessBoundaryUp$ packet factors through the refused representative surface $E,A,V$ and the admitted $\psame$ transport surface $E,T,H,C,P,N$. This factorization is total for the downstream nonimport boundary: no downstream consumer imports quotient carriers, representative selectors, quotient equality eliminators, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundary\_downstream\_nonimport\_totality}
\begin{proof}
First apply public bridge non-escape, \autoref{thm:quotient-soundness-boundary-public-bridge-nonescape}. It keeps every consumer read inside $E,A,T,V,H,C,P,N$ and gives no bridge coordinate for the excluded quotient primitives.

Next use erased derivation refusal and psame-only descent, \autoref{thm:quotient-soundness-boundary-erased-derivation-refusal} and \autoref{thm:quotient-soundness-boundary-psame-only-descent}. The representative-side demand is routed to $E,A,V$ and refused before the admitted positive motion is read as classifier-respecting $\psame$ transport through $E,T,H,C,P,N$.

Finally cite the root nonimport ledger, \autoref{thm:quotient-soundness-boundary-root-nonimport-ledger}. The root ledger already packages the same refusal surface and positive transport surface without quotient carriers, representative selectors, quotient equality eliminators, erased derivation recovery, host quotient recursion, or $\mathsf{Quot.sound}$, so the downstream consumer has no additional import route.
\end{proof}

\begin{theorem}[QuotientSoundnessBoundary kernel dependency route]
\label{thm:quotient-soundness-boundary-kernel-dependency-route}
The downstream nonimport scope of $\QuotientSoundnessBoundaryUp$ is read first through \autoref{ch:concrete-instances-negative-name-boundary-namecert} for representative-refusal discipline and then through \autoref{ch:concrete-instances-hostprimitiveleakage-namecert} for host-primitive leakage refusal. Only after those sibling boundaries are visible does the local quotient-soundness packet replace quotient elimination with displayed $\psame$ transport through $E,T,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.QuotientSoundnessBoundaryUp.QuotientSoundnessBoundaryKernelDependencyRoute}
\begin{proof}
Start with the downstream nonimport totality theorem above. It keeps downstream consumers inside the refused representative surface $E,A,V$ and the admitted $\psame$ transport surface $E,T,H,C,P,N$.

Read the negative-name sibling first. The refusal discipline of \autoref{ch:concrete-instances-negative-name-boundary-namecert} classifies representative recovery as a boundary request rather than as supplied quotient content.

Read the host-primitive sibling next. The leakage refusal of \autoref{ch:concrete-instances-hostprimitiveleakage-namecert} prevents the same request from being reintroduced as a host primitive, host quotient recursion, or $\mathsf{Quot.sound}$ witness.

Finally apply public bridge non-escape and psame consumer factorization. The surviving route is displayed $\psame$ transport inside the local rows, so the dependency route has no escape into quotient elimination or host-side primitive supply.
\end{proof}
