\begin{theorem}[KernelCategory carrier admission obligation]
\label{thm:kernel-category-carrier-admission-obligation}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, carrier admission is
exactly the finite obligation surface consisting of unary object histories in
$O$, continuation-ledger hom rows in $H$, empty-continuation identity rows in
$I$, displayed $\Cont$ composites in $C$, componentwise $\hsame$ law transports
in $A$ and $U$, provenance in $P$, and local $\NameCert$ in $N$. It admits no
host category object, quotient morphism, external arrow equality, functor
semantics, natural transformation, limit object, or global naming row outside
that tuple.
\end{theorem}
\begin{proof}
Start with \autoref{def:kernel-category-carrier}. Its carrier tuple exposes
the object, hom, identity, composition, law-transport, provenance, and local
naming rows as the available finite packet.

Use \autoref{thm:kernel-category-identity-continuation} for the identity side.
It identifies identity admission with empty continuation rows over unary object
histories already present in $O$.

Use \autoref{thm:kernel-category-composition-continuation} for the hom side.
It identifies composition admission with displayed $\Cont$ composites whose
endpoints remain in the continuation-ledger hom rows of $H$.

Finally apply \autoref{thm:kernel-category-certificate-surface} and
\autoref{thm:kernel-category-pkg-provenance-nonescape}. The certificate and
provenance rows expose the $\hsame$ law transports, package row, and local
naming row, while their non-escape clauses exclude all host category and
quotient coordinates outside $K$.
\end{proof}
\leanchecked{BEDC.Derived.KernelCategoryUp.KernelCategoryCarrier\_carrier\_admission\_obligation}

\begin{theorem}[KernelCategory continuation route factorization]
\label{thm:kernel-category-cont-route-factorization}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, every admitted
composition route factors through unary object histories in $O$,
continuation-ledger hom rows in $H$, displayed $\Cont$ composites in $C$,
componentwise $\hsame$ transports in $A$ and $U$, $\Pkg$ provenance in $P$,
and the local $\NameCert$ row $N$. It has no factor through host category
composition, quotient morphisms, external arrow equality, functorial
semantics, natural transformations, limits, or a second naming source.
\end{theorem}
\begin{proof}
Start with \autoref{thm:kernel-category-carrier-admission-obligation}. It
fixes $O,H,I,C,A,U,P,N$ as the complete carrier-admission surface and leaves no
composition-shaped coordinate outside that tuple.

Use \autoref{thm:kernel-category-composition-continuation}. Any composition
read is a displayed $\Cont$ composite whose endpoints and inputs already live
in the unary object and continuation-ledger hom rows.

The law part of the factorization is supplied by
\autoref{thm:kernel-category-certificate-surface}. Associativity and unit
comparisons are componentwise $\hsame$ transports over the displayed rows, not
host arrow equalities.

Finally apply \autoref{thm:kernel-category-pkg-provenance-nonescape}. The
$\Pkg$ and local $\NameCert$ rows record only provenance and naming for the
finite BEDC packet, so every admitted route has the displayed factorization
and no external category route remains.
\end{proof}

\begin{theorem}[KernelCategory continuation handoff for CategoryUp]
\label{thm:kernel-category-category-continuation-handoff}
Any $\CategoryUp$ consumer of the $\KernelCategoryUp$ packet receives only the
finite continuation rows already displayed in the category, unary
continuation-monoid, and continuation-monad constructions of
\autoref{ch:concrete-instances-category-namecert},
\autoref{ch:concrete-instances-unarycontmonoid-namecert}, and
\autoref{ch:concrete-instances-continuationmonad-namecert}. The handoff
exports object histories, hom ledgers, empty-continuation identity rows,
displayed $\Cont$ composites, $\hsame$ law transports, $\Pkg$ provenance, and
local $\NameCert$ naming, but not host category objects, quotient morphisms, or
external arrow equality.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:kernel-category-carrier-admission-obligation}. The
consumer can read only the finite packet rows $O,H,I,C,A,U,P,N$.

Apply \autoref{thm:kernel-category-identity-continuation}. The identity rows
handed to the consumer are empty-continuation rows over unary object histories,
matching the unary continuation-monoid and continuation-monad sources.

Apply \autoref{thm:kernel-category-composition-continuation}. The composition
rows handed to the consumer are displayed $\Cont$ composites of
continuation-ledger hom rows, matching the category-side finite continuation
surface.

Finally use \autoref{thm:kernel-category-certificate-surface} and
\autoref{thm:kernel-category-pkg-provenance-nonescape}. These rows package the
$\hsame$ law transports, provenance, and local naming while blocking any host
category object, quotient morphism, or external arrow equality from entering
the $\CategoryUp$ read.
\end{proof}

\begin{theorem}[KernelCategory downstream consumer readiness]
\label{thm:kernel-category-downstream-consumer-readiness}
Downstream Functor, NatTrans, and Category consumers may cite the
$\KernelCategoryUp$ carrier, identity rows, composition rows, law-transport
rows, package provenance, and non-escape rows as a complete BEDC kernel
surface. Such consumers need not import host category objects, quotient
morphisms, external arrow equality, functorial semantics, natural
transformation objects, limit objects, adjunction data, or a global naming
row beyond the local $\NameCert$ row.
\end{theorem}
\begin{proof}
First read the carrier through \autoref{def:kernel-category-carrier} and
\autoref{thm:kernel-category-carrier-admission-obligation}. These fix the
finite rows available to every downstream consumer.

Next use \autoref{thm:kernel-category-identity-continuation} and
\autoref{thm:kernel-category-composition-continuation}. Identity and
composition are already displayed as empty-continuation rows and $\Cont$
composites, so a downstream consumer has the operation rows it needs without a
host category object.

The law rows are supplied by \autoref{thm:kernel-category-certificate-surface}.
They transport associativity and units through componentwise $\hsame$ rows,
which is enough for Category, Functor, and NatTrans consumers to cite the
kernel packet as their operation surface.

Finally apply \autoref{thm:kernel-category-pkg-provenance-nonescape}. The
package and non-escape rows keep provenance and naming local to $P,N$, so the
consumer has no route to quotient morphisms, external arrow equality, limits,
adjunctions, or a global naming row.
\end{proof}

\begin{theorem}[KernelCategory root hom-law triad]
\label{thm:kernel-category-root-hom-law-triad}
Every root consumer of a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$ must read the hom ledger $H$, the identity row $I$, and the composition row $C$ before it reads associativity or unit law rows in $A$ and $U$. The law rows therefore compare already displayed continuation-ledger operations; they do not introduce host category composition, quotient morphisms, external arrow equality, functorial semantics, natural transformations, or limit objects.
\end{theorem}
\begin{proof}
Start with \autoref{thm:kernel-category-carrier-admission-obligation}. It fixes $O,H,I,C,A,U,P,N$ as the full root admission surface and places hom, identity, and composition data in the displayed packet before the law transports are consumed.

Apply \autoref{thm:kernel-category-identity-continuation}. Identity rows are empty-continuation reads over unary object histories, so a unit-law read has no host identity operation to import.

Apply \autoref{thm:kernel-category-composition-continuation}. Composition rows are displayed $\Cont$ composites between continuation-ledger hom rows, so an associativity read must already have passed through $H$ and $C$.

Finally use \autoref{thm:kernel-category-certificate-surface}. It supplies $A$ and $U$ as componentwise $\hsame$ law transports over those displayed rows, while \autoref{thm:kernel-category-pkg-provenance-nonescape} removes every host or quotient category coordinate outside the packet.
\end{proof}

\begin{theorem}[KernelCategory root endpoint exhaustion]
\label{thm:kernel-category-root-endpoint-exhaustion}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, every displayed $\Cont$ composite through the object row $O$, hom ledger $H$, identity row $I$, and composition row $C$ has endpoints exhausted by the unary object histories in $O$ and the continuation-ledger hom rows in $H$. No endpoint can be supplied by a host category object, quotient morphism, external arrow equality, functor semantic row, natural transformation, or limit object.
\end{theorem}
\begin{proof}
Read the composite through \autoref{thm:kernel-category-composition-continuation}. It builds each composite from continuation-ledger hom rows in $H$ and a displayed $\Cont$ composition row in $C$.

Use \autoref{thm:kernel-category-identity-continuation} for endpoint identities. The identity rows in $I$ are empty-continuation reads over unary object histories, so their endpoints are already in $O$.

Apply \autoref{thm:kernel-category-cont-composition-locality}. Locality keeps the displayed composite inside the same endpoint and hom ledgers rather than moving through a host category composition operation.

Finish with \autoref{thm:kernel-category-certificate-surface} and \autoref{thm:kernel-category-pkg-provenance-nonescape}. Their non-escape clauses exclude host endpoints, quotient endpoints, external arrow equality, functor semantics, natural transformations, and limits from the root endpoint surface.
\end{proof}

\begin{theorem}[KernelCategory root non-escape surface]
\label{thm:kernel-category-root-nonescape-surface}
The root public surface of a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$ is exhausted by unary object histories, continuation-ledger hom rows, empty-continuation identities, displayed $\Cont$ composites, componentwise $\hsame$ law transports, $\Pkg$ provenance, and the local $\NameCert$ row. It exports no host category object, quotient morphism, external arrow equality, functor semantics, natural transformation, limit object, or detached global category certificate.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:kernel-category-carrier-admission-obligation}. The theorem identifies the displayed packet rows $O,H,I,C,A,U,P,N$ and excludes additional category-shaped coordinates from carrier admission.

Use \autoref{thm:kernel-category-certificate-surface}. The certificate surface supplies exactly the local naming and law-transport reads needed by the root packet.

Use \autoref{thm:kernel-category-cont-composition-locality}. Any composite that reaches the public surface remains a displayed $\Cont$ composite over local endpoint and hom rows.

Finally apply \autoref{thm:kernel-category-pkg-provenance-nonescape}. The provenance row is local to the packet and cannot be reread as host category data, quotient morphism data, functorial semantics, natural transformations, limits, or a second global naming source.
\end{proof}

\begin{theorem}[KernelCategory root public readiness]
\label{thm:kernel-category-root-public-readiness}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, the public root surface is ready exactly when every root read is a displayed $\BHist$ read of unary object histories in $O$, continuation-ledger hom rows in $H$, empty-continuation identity rows in $I$, displayed $\Cont$ composites in $C$, componentwise $\hsame$ law transports in $A$ and $U$, $\Pkg$ provenance in $P$, and the local $\NameCert$ row in $N$. The surface contains no host category object, quotient morphism, external arrow equality, functorial semantics, natural transformation, limit object, or global naming source outside those rows.
\end{theorem}
\begin{proof}
Project from \autoref{def:kernel-category-carrier}. The carrier exposes only the rows $O,H,I,C,A,U,P,N$, with object reads carried by unary $\BHist$ histories and hom reads carried by continuation ledgers.

Apply \autoref{thm:kernel-category-identity-continuation} and \autoref{thm:kernel-category-composition-continuation}. Identity readiness is the empty $\Cont$ route over a unary history, and composition readiness is the displayed $\Cont$ composite over hom ledger rows.

Use \autoref{thm:kernel-category-associativity-scope} and \autoref{thm:kernel-category-unit-scope} for the law rows. These theorems place associativity and unit comparisons in the componentwise $\hsame$ transports $A$ and $U$.

Finally apply \autoref{thm:kernel-category-certificate-surface}, \autoref{thm:kernel-category-pkg-provenance-nonescape}, and \autoref{thm:kernel-category-carrier-admission-obligation}. The package and naming rows are therefore local to $P,N$, and every public root read is already accounted for by the displayed packet.
\end{proof}

\begin{theorem}[KernelCategory downstream consumer totality]
\label{thm:kernel-category-downstream-consumer-totality}
Every downstream consumer of a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$ is total on the displayed BEDC rows of $K$ precisely by reading unary $\BHist$ object histories, continuation-ledger hom histories, displayed $\Cont$ identity and composition routes, componentwise $\hsame$ law transports, $\Pkg$ provenance, and the local $\NameCert$ row. No downstream consumer may demand a host category carrier, quotient morphism, external equality of arrows, natural-transformation coordinate, limit object, or second certificate before it can read the packet.
\end{theorem}
\begin{proof}
Start with \autoref{thm:kernel-category-carrier-admission-obligation}. It gives the finite admission surface on which a consumer may be total: $O,H,I,C,A,U,P,N$ and no additional category-shaped row.

Read the operation rows next. By \autoref{thm:kernel-category-identity-continuation}, identity consumption is total for empty continuation rows over unary object histories. By \autoref{thm:kernel-category-composition-continuation}, composition consumption is total for displayed $\Cont$ composites over continuation-ledger hom rows.

The law rows are then supplied by \autoref{thm:kernel-category-associativity-scope}, \autoref{thm:kernel-category-unit-scope}, and \autoref{thm:kernel-category-law-transport-exhaustion}. They make the consumer read only the componentwise $\hsame$ transports $A$ and $U$.

Finally use \autoref{thm:kernel-category-certificate-surface} and \autoref{thm:kernel-category-pkg-provenance-nonescape}. Since $\Pkg$ provenance and the local $\NameCert$ row are the only certificate endpoints, the downstream route is total on the displayed packet and nowhere else.
\end{proof}

\begin{theorem}[KernelCategory formal-target frontier]
\label{thm:kernel-category-formal-target-frontier}
The formal target frontier for $\KernelCategoryUp$ is the concrete packet $K=(O,H,I,C,A,U,P,N)$ together with its BEDC rows: $\BHist$ unary object histories, continuation-ledger hom histories, displayed $\Cont$ identity and composition routes, componentwise $\hsame$ associativity and unit transports, $\Pkg$ provenance, and local $\NameCert$ naming. Formalization of the public root claim needs exactly carrier admission, identity continuation, composition continuation, law transport, provenance non-escape, and local certificate exhaustion for those rows, and it needs no host category semantics or quotient arrow equality.
\end{theorem}
\begin{proof}
The frontier begins at \autoref{def:kernel-category-carrier}: the only data offered to Lean-side reconstruction is the packet $O,H,I,C,A,U,P,N$.

Use \autoref{thm:kernel-category-carrier-admission-obligation} to identify the admission clauses. This separates unary object histories, hom ledgers, identity rows, composition rows, law transports, provenance, and local naming as the proof obligations.

Then compose the existing operation and law theorems. The identity and composition clauses are \autoref{thm:kernel-category-identity-continuation} and \autoref{thm:kernel-category-composition-continuation}; the law clauses are \autoref{thm:kernel-category-associativity-scope}, \autoref{thm:kernel-category-unit-scope}, and \autoref{thm:kernel-category-law-transport-exhaustion}.

The frontier closes with \autoref{thm:kernel-category-certificate-surface} and \autoref{thm:kernel-category-pkg-provenance-nonescape}. These show that $\Pkg$ provenance and the local $\NameCert$ row are the final public coordinates, while every host or quotient category object remains outside the formal target.
\end{proof}

\begin{theorem}[KernelCategory root transport non-escape]
\label{thm:kernel-category-root-transport-nonescape}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, every endpoint and hom transport remains inside the displayed rows $O,H,I,C,A,U,P,N$. Endpoint transport reads unary object histories in $O$, hom transport reads continuation-ledger hom rows in $H$, and law transport reads only the componentwise $\hsame$ rows in $A$ and $U$ together with the displayed $\Cont$, $\Pkg$, and local $\NameCert$ support. No host category object, quotient morphism, external arrow equality, functorial semantic row, natural transformation, or limit object is available.
\end{theorem}
\leanchecked{BEDC.Derived.KernelCategoryUp.KernelCategoryCarrier\_root\_transport\_nonescape}
\begin{proof}
Start with the carrier admission obligation, \autoref{thm:kernel-category-carrier-admission-obligation}. It fixes the finite packet rows $O,H,I,C,A,U,P,N$ as the full admission surface.

Apply \autoref{thm:kernel-category-identity-continuation} to endpoint identities and \autoref{thm:kernel-category-composition-continuation} to hom composites. These theorems keep identity and composition reads in unary object histories, continuation-ledger hom rows, and displayed $\Cont$ composites.

Finally use \autoref{thm:kernel-category-certificate-surface} and \autoref{thm:kernel-category-pkg-provenance-nonescape}. The certificate rows supply the componentwise law transports, and the provenance theorem removes host category objects, quotient morphisms, external equality, and all category-shaped structure outside the packet.
\end{proof}

\begin{theorem}[KernelCategory public consumer triad]
\label{thm:kernel-category-public-consumer-triad}
Every public consumer of a $\KernelCategoryUp$ packet must pass through three admission gates before reading associativity or unit law rows:
\begin{enumerate}
\item carrier admission for the object, hom, identity, composition, law-transport, provenance, and local naming rows;
\item identity-continuation admission for empty-continuation identity rows over unary object histories;
\item composition-continuation admission for displayed $\Cont$ composites between continuation-ledger hom rows.
\end{enumerate}
Only after these three gates may the consumer read the $A$ and $U$ law-transport rows. The route imports no host category object, quotient morphism, external arrow equality, functorial semantics, natural transformation, limit object, or second naming source.
\end{theorem}
\begin{proof}
First use \autoref{thm:kernel-category-carrier-admission-obligation}. It exposes the finite carrier surface and blocks public reads outside $O,H,I,C,A,U,P,N$.

Next apply \autoref{thm:kernel-category-identity-continuation}. The identity side of a public consumer is admitted only through empty $\Cont$ rows attached to unary object histories.

Then apply \autoref{thm:kernel-category-composition-continuation}. The composition side is admitted only through displayed $\Cont$ composites built from continuation-ledger hom rows.

With the three gates in place, \autoref{thm:kernel-category-certificate-surface} supplies the associativity and unit transports, and \autoref{thm:kernel-category-pkg-provenance-nonescape} supplies the provenance non-escape clause. Thus the law rows are consumed only after carrier, identity, and composition admission, with no host or quotient route added.
\end{proof}

\begin{theorem}[KernelCategory hom ledger exhaustion]
\label{thm:kernel-category-hom-ledger-exhaustion}
For a $\KernelCategoryUp$ packet $K=(O,H,I,C,A,U,P,N)$, every hom read is exhausted by unary endpoints in $O$, continuation-ledger hom rows in $H$, displayed $\Cont$ composites in $C$, componentwise $\hsame$ transports in $A$ and $U$, $\Pkg$ provenance in $P$, and the local $\NameCert$ row $N$. A hom consumer has no extra coordinate for host morphisms, quotient morphisms, external equality of arrows, functorial semantics, natural transformations, limits, or a detached global category.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:kernel-category-carrier-admission-obligation}. It identifies the hom ledger as part of the same finite packet as the unary object endpoints, law transports, provenance, and local naming row.

Use \autoref{thm:kernel-category-composition-continuation}. Every composite hom read is a displayed $\Cont$ composite of continuation-ledger hom rows whose endpoints are already in $O$ and $H$.

Use \autoref{thm:kernel-category-identity-continuation} for identity hom rows. These are empty-continuation reads over unary object histories, so they add no host identity morphism.

Finally apply \autoref{thm:kernel-category-certificate-surface} and \autoref{thm:kernel-category-pkg-provenance-nonescape}. The $\hsame$, $\Pkg$, and local $\NameCert$ rows exhaust the public certificate surface and exclude every host, quotient, functorial, limit, or detached category coordinate.
\end{proof}

\begin{theorem}[KernelCategory continuation composition stability]
\label{thm:kernel-category-cont-composition-stability}
Let $K=(O,H,I,C,A,U,P,N)$ and $K'=(O',H',I',C',A',U',P',N')$ be
$\KernelCategoryUp$ packets whose endpoints and hom rows are related by
componentwise $\hsame$ transports. Any displayed $\Cont$ composite admitted by
$C$ transports to the corresponding displayed $\Cont$ composite admitted by
$C'$ using only the endpoint rows, hom rows, and law transports of the two
packets. The stability statement has no coordinate for host category
composition, quotient morphism, or external equality of arrows.
\end{theorem}
\begin{proof}
Read composition through \autoref{thm:kernel-category-cont-composition-locality}.
It says that a composition read is local to displayed $\Cont$ rows and the
endpoint ledgers already present in $O$ and $H$.

Apply \autoref{thm:kernel-category-composition-continuation}. The composite
hom row is constructed from the two input continuation-ledger hom rows and the
displayed $\Cont$ composite row joining them.

The componentwise $\hsame$ endpoint and hom transports move those input rows
from $K$ to $K'$. The associativity and unit transports in $A,U,A',U'$ compare
only displayed continuation ledgers, so the transported composite remains a
displayed $\Cont$ composite rather than a host category composition.

Finally use \autoref{thm:kernel-category-certificate-surface}. Its non-escape
clause removes quotient morphisms and external arrow equality, leaving the
displayed continuation route as the entire stability witness.
\end{proof}
\leanchecked{BEDC.Derived.KernelCategoryUp.KernelCategoryCarrier\_cont\_composition\_stability}

\begin{theorem}[KernelCategory NameCert route exhaustion]
\label{thm:kernel-category-namecert-route-exhaustion}
Every public read of a $\KernelCategoryUp$ packet factors through carrier
admission, identity continuation, composition continuation, associativity and
unit transports, package provenance, and local naming. Thus the local
$\NameCert$ route is exhausted by the rows $O,H,I,C,A,U,P,N$ and exports no
host category universe, quotient morphism, external arrow equality, functorial
semantics, natural transformation, limit object, adjunction, or second naming
source.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:kernel-category-carrier-admission-obligation}. It fixes the
available carrier rows as unary object histories, continuation-ledger hom
rows, identity rows, displayed composites, law transports, provenance, and
local naming.

Next use \autoref{thm:kernel-category-identity-continuation} and
\autoref{thm:kernel-category-composition-continuation}. These identify the two
operation routes available to a public read and keep both routes inside the
displayed continuation ledger.

The law rows are supplied by \autoref{thm:kernel-category-certificate-surface}.
They transport associativity and unit comparisons through $\hsame$ rows rather
than through external equality of arrows.

Finally apply \autoref{thm:kernel-category-pkg-provenance-nonescape}. The
provenance row records only the finite BEDC carrier and local NameCert route,
so all host category, quotient, functorial, limit, adjunction, and second
naming coordinates are outside the public read.
\end{proof}

