\chapter{A Concrete Naming Certificate for $\TrieUp$}
\label{ch:concrete-instances-trie-namecert}
\origin{human}

The $\TrieUp$ interface names finite prefix-indexed data without importing host
strings, host maps, or a host trie primitive. The reference point is Okasaki,
\emph{Purely Functional Data Structures} (1998), where tries are finite
prefix trees for keyed lookup; the BEDC surface below reads that structure as
finite $\BoolUp$, $\ListUp$, $\OptionUp$, $\NatUp$, and $\BitVectorUp$ rows.

The concrete dependency route consumes
\autoref{ch:concrete-instances-bool-namecert} for branch tags,
\autoref{ch:concrete-instances-list-namecert} and
\autoref{ch:concrete-instances-bitvector-namecert} for finite key paths,
\autoref{ch:concrete-instances-option-namecert} for terminal payload rows, and
\autoref{ch:concrete-instances-nat-namecert} for depth bounds.

\begin{definition}[Trie BHist source]\label{def:trie-bhist-source}
A $\TrieUp$ source packet is a finite $\mathsf{BHist}$ record
$$
T=(k,v,l,b,p)
$$
with the following visible coordinates:
\begin{enumerate}
\item $k$ is a finite key-path row, read either as a $\BitVectorUp$ path or as
a $\ListUp$ spine of branch histories;
\item $v$ is an $\OptionUp$ terminal payload row, recording whether the
current prefix carries a value and, when present, exposing only the displayed
value row;
\item $l$ is a $\NatUp$ length and depth ledger recording the finite prefix
length, the depth of each inspected node, and the fact that every public read
is below that depth;
\item $b$ is the branch ledger whose branch tags are $\BoolUp$ rows and whose
left and right subprefix reads are routed only through displayed finite list
or bit-vector positions;
\item $p$ is the $\Pkg$ provenance naming the consumed $\BoolUp$, $\ListUp$,
$\OptionUp$, $\NatUp$, $\BitVectorUp$, $\hsame$, and $\Cont$ certificate rows.
\end{enumerate}
The carrier predicate is $\mathsf{TrieSource}(k,v,l,b,p)$. Its classifier
compares accepted packets by componentwise key-path comparison, optional
payload comparison, branch-tag comparison, length-ledger comparison, and the
same displayed $\hsame$, $\Cont$, and $\Pkg$ routes. The packet contains no
host string equality, host finite map, function extensionality, hidden
ordering on keys, or unbounded tree object.
\end{definition}

\begin{theorem}[Trie carrier stability]\label{thm:trie-carrier-stability}
Let $T=(k,v,l,b,p)$ be an accepted $\TrieUp$ source packet. If the key path,
optional payload, depth ledger, branch ledger, and provenance row are
transported by displayed $\hsame$ along the $\Cont$ routes named by $p$, then
the transported packet $T'=(k',v',l',b',p')$ is again an accepted $\TrieUp$
source packet.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_carrier\_stability}
\leanvariant{BEDC.Derived.TrieUp.TriePacket\_carrier\_stability}
\begin{proof}
Project the five coordinates of \autoref{def:trie-bhist-source}. The
$\NatUp$ ledger transports first, so every later prefix and branch read is
bounded by the transported finite depth row.

Transport the key row through its displayed $\BitVectorUp$ or $\ListUp$
presentation. Each branch tag is a $\BoolUp$ row, so the branch ledger
transports componentwise along the same key-path positions.

Finally transport the optional payload and provenance rows. The $\OptionUp$
row preserves the absent case and transports the present payload only when the
present tag is displayed, while the $\Pkg$ row keeps the same finite
certificate dependencies. Thus the transported record is another accepted
trie source packet.
\end{proof}

\begin{theorem}[Trie classifier laws]\label{thm:trie-classifier-laws}
The $\TrieUp$ classifier is reflexive, symmetric, and transitive on accepted
packets by componentwise use of the $\BitVectorUp$ or $\ListUp$ key-path
classifier, the $\OptionUp$ payload classifier, the $\BoolUp$ branch
classifier, and the $\NatUp$ ledger classifier.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_classifier\_laws}
\begin{proof}
For reflexivity, take the reflexive classifier row for the key path, the
optional payload, each boolean branch tag, and the finite depth ledger. The
provenance and continuation rows are read unchanged.

For symmetry, reverse each displayed component comparison. The absent and
present cases of the optional payload reverse by the $\OptionUp$ classifier,
and every branch tag reverses by the $\BoolUp$ classifier.

For transitivity, compose the two key-path comparisons, the two optional
payload comparisons, the two branch-ledger comparisons, and the two depth
ledger comparisons. The depth ledger fixes the finite set of visible prefix
positions, so no hidden branch can enter the composite classifier.
\end{proof}

\begin{theorem}[Trie ledger coverage]\label{thm:trie-ledger-coverage}
Every public read of an accepted $\TrieUp$ packet factors through the finite
ledger $(k,v,l,b,p)$. Consumers see exactly finite prefix rows, boolean branch
rows, optional terminal payload rows, depth and length rows, $\hsame$
transports, $\Cont$ routes, and $\Pkg$ provenance.

Consequently the packet exports no host string type, host map lookup, ambient
function space, infinite tree, or implicit key ordering.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_ledger\_coverage}
\begin{proof}
Start from the carrier definition. Its tuple lists exactly the key, terminal
payload, depth ledger, branch ledger, and provenance coordinates.

A prefix-facing consumer reads $k$ through the displayed $\BitVectorUp$ or
$\ListUp$ path. A branch-facing consumer reads $b$ only through the boolean
tags admitted by the finite depth ledger $l$. A value-facing consumer reads
$v$ only through the $\OptionUp$ absent-or-present row.

The remaining public reads are the displayed $\hsame$ comparisons, $\Cont$
routes, and $\Pkg$ provenance named in $p$. Since no further coordinate is
present, every consumer projection is one of these finite rows.
\end{proof}

\begin{theorem}[Trie prefix-branch exactness]
\label{thm:trie-obligation-prefix-branch-exactness}
Every public branch read at a displayed finite prefix of an accepted $\TrieUp$
packet is determined by the key path row, the $\NatUp$ depth ledger, the
$\BoolUp$ branch tag at that prefix, the optional payload row, visible
$\hsame$ transport, $\Cont$ routes, and $\mathsf{Pkg}$ provenance from
\autoref{def:trie-bhist-source}.

No host string equality, host map lookup, hidden branch coordinate, or infinite
tree can change the read.
\end{theorem}
\begin{proof}
Project the tuple $(k,v,l,b,p)$ from \autoref{def:trie-bhist-source}. The key
path row $k$, optional payload row $v$, depth ledger $l$, branch ledger $b$,
and provenance row $p$ are the only coordinates admitted by the accepted
packet.

Use \autoref{thm:trie-ledger-coverage} to bound public branch reads by the
finite prefix rows displayed below the depth ledger. A consumer at such a
prefix can inspect only the recorded branch tag, the corresponding key-path
coordinate, the optional terminal payload row, and the visible transport and
provenance rows.

Finally apply \autoref{thm:trie-classifier-laws} componentwise. Transport of
the key, branch, payload, and depth rows preserves exactly the displayed finite
coordinates, so the $\NameCert$ surface of
\autoref{thm:trie-namecert-obligation-surface} receives a branch read whose
value is fixed by the recorded rows and by no host-side tree structure.
\end{proof}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_prefix\_branch\_exactness}

\begin{theorem}[Trie prefix branch consumer exhaustion]
\label{thm:trie-prefix-branch-consumer-exhaustion}
Any accepted $\TrieUp$ prefix-branch consumer read factors through the displayed
finite $\mathsf{BHist}$ prefix row, the $\BoolUp$ branch tag, the $\ListUp$ path
spine, the $\NatUp$ depth counter, the $\OptionUp$ terminal payload row,
displayed $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
the local $\NameCert_{\TrieUp}$ ledger.

The consumer surface is exactly this finite BEDC row surface. It exports no
host map, external tree equality, unbounded lookup function, hidden node object,
or host key ordering.
\end{theorem}
\begin{proof}
Project the source tuple $(k,v,l,b,p)$ of
\autoref{def:trie-bhist-source}. The key coordinate supplies the displayed
finite prefix row as a $\ListUp$ spine, the branch ledger supplies the
$\BoolUp$ branch tag, the depth coordinate supplies the $\NatUp$ counter, and
the terminal coordinate supplies the $\OptionUp$ payload row.

Use \autoref{thm:trie-obligation-prefix-branch-exactness} to bind a public
prefix-branch read to those coordinates. Its route records the same displayed
$\hsame$ transports, $\Cont$ routes, and $\mathsf{Pkg}$ provenance named by the
source packet.

Repack the resulting finite read through
\autoref{thm:trie-namecert-obligation-surface}. The local $\NameCert_{\TrieUp}$
ledger accepts exactly the carrier rows, classifier rows, prefix-branch
determinacy rows, transport rows, and ledger-exactness rows already displayed
in the packet.

Apply \autoref{thm:trie-ledger-coverage} for the exclusion claim. Since every
consumer projection is a row of $(k,v,l,b,p)$ or the named local certificate
ledger, no host map, external tree equality, unbounded lookup function, hidden
node object, or host key ordering is exported.
\end{proof}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_prefix\_branch\_consumer\_exhaustion}

\begin{theorem}[Trie key-path exhaustion]\label{thm:trie-key-path-exhaustion}
Every public key-path read of an accepted $\TrieUp$ packet is exhausted by
the displayed $\BitVectorUp$ or $\ListUp$ key row, the $\NatUp$ depth ledger,
the $\hsame$ transports and $\Cont$ routes named by the packet, and the
$\Pkg$ provenance row. No host string, host ordering, ambient finite map, or
hidden key predicate contributes an additional public key-path coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_key\_path\_route\_exhaustion}
\begin{proof}
Project the key coordinate $k$ and depth ledger $l$ from
\autoref{def:trie-bhist-source}. The definition gives $k$ only as a displayed
$\BitVectorUp$ path or as a $\ListUp$ spine of branch histories, and it gives
$l$ as the bound for every public prefix read.

Use \autoref{thm:trie-carrier-stability} to see that transport preserves this
same finite key presentation along the displayed $\hsame$ and $\Cont$ routes.
Then apply \autoref{thm:trie-classifier-laws} componentwise to the accepted
key rows.

Finally apply \autoref{thm:trie-ledger-coverage}. Since every public read is
a projection from $(k,v,l,b,p)$, the only remaining key-path data is the
provenance named in $p$, and no host key structure is exported.
\end{proof}

\begin{theorem}[Trie prefix-branch determinacy]\label{thm:trie-prefix-branch-determinacy}
At each displayed finite prefix below the $\NatUp$ depth row of an accepted
$\TrieUp$ packet, the $\BoolUp$ branch tag selects exactly the recorded left
or right subprefix. No unrecorded branch at that prefix is public.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_prefix\_branch\_determinacy}
\begin{proof}
Project the branch ledger $b$ and the depth ledger $l$ from
\autoref{def:trie-bhist-source}. The ledger $l$ bounds the finite prefix
positions that a consumer may inspect, and $b$ records branch tags only at
those displayed positions.

For any such prefix, read the branch tag through its $\BoolUp$ row. The two
displayed boolean cases select the recorded left or right subprefix row, and
\autoref{thm:trie-classifier-laws} transports equality of branch reads
componentwise through the same finite coordinates.

The stability theorem \autoref{thm:trie-carrier-stability} preserves the
branch ledger under $\hsame$ and $\Cont$. Applying
\autoref{thm:trie-ledger-coverage} then excludes any branch coordinate not
recorded in $(k,v,l,b,p)$, so no extra branch is public.
\end{proof}

\begin{theorem}[Trie lookup payload projection]\label{thm:trie-lookup-payload-projection}
Every lookup payload read of an accepted $\TrieUp$ packet factors through the
$\OptionUp$ absent-or-present terminal row at the displayed key path. The
read never factors through a host finite map, host lookup function, or ambient
function space.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_lookup\_payload\_projection}
\begin{proof}
Project the terminal payload coordinate $v$ from
\autoref{def:trie-bhist-source}. The coordinate is an $\OptionUp$ row at the
displayed key path, so a consumer can observe only the absent tag or the
present tag together with the displayed payload row.

The key path used by the lookup is fixed by
\autoref{thm:trie-key-path-exhaustion}. The payload row transports along the
same displayed $\hsame$ and $\Cont$ routes by
\autoref{thm:trie-carrier-stability}, and the accepted-row comparison is
componentwise by \autoref{thm:trie-classifier-laws}.

Apply \autoref{thm:trie-ledger-coverage} to close the projection. Since the
finite tuple exports no host map or function coordinate, lookup payload reads
can only pass through the displayed $\OptionUp$ terminal row.
\end{proof}

\begin{theorem}[Trie NameCert obligation surface]\label{thm:trie-namecert-obligation-surface}
The local $\NameCert_{\TrieUp}$ obligation surface consists of five finite
rows:
\begin{enumerate}
\item carrier habitation: the empty trie is carried by the empty key path, an
absent $\OptionUp$ payload, the zero $\NatUp$ depth ledger, the empty branch
ledger, and the corresponding $\Pkg$ provenance;
\item classifier laws: reflexivity, symmetry, and transitivity are inherited
componentwise from \autoref{thm:trie-classifier-laws};
\item prefix-branch determinacy: at each displayed finite prefix, a $\BoolUp$
branch tag selects exactly the recorded left or right subprefix row, and no
unrecorded branch is public, as witnessed by
\autoref{thm:trie-key-path-exhaustion} and
\autoref{thm:trie-obligation-prefix-branch-exactness};
\item transport under $\hsame$ and $\Cont$: the stability theorem
\autoref{thm:trie-carrier-stability} repacks transported key, payload, branch,
ledger, and provenance rows as another accepted packet, with lookup payload
projection fixed by \autoref{thm:trie-lookup-payload-projection};
\item ledger exactness: downstream consumers may read only finite prefix
rows, branch rows, optional terminal payload rows, length and depth rows, and
the displayed provenance rows of \autoref{thm:trie-ledger-coverage}, with the
key-path, branch, and payload projections separated by
\autoref{thm:trie-key-path-exhaustion},
\autoref{thm:trie-prefix-branch-determinacy}, and
\autoref{thm:trie-lookup-payload-projection}.
\end{enumerate}
These rows are the complete seed obligation surface for prefix-tree
NameCert data over finite BEDC rows.
\end{theorem}
\leanchecked{BEDC.Derived.TrieUp.TrieSourcePacket\_namecert\_obligation\_surface}
\begin{proof}
For carrier habitation, choose the empty $\BitVectorUp$ or empty $\ListUp$
path, the absent $\OptionUp$ payload, the zero $\NatUp$ depth row, and the
empty branch ledger. The provenance row records only the finite data
certificates consumed by the packet.

For the classifier laws, apply \autoref{thm:trie-classifier-laws}. Because the
classifier is componentwise, the three equivalence laws are inherited from the
key, option, boolean branch, and natural ledger classifiers.

For prefix-branch determinacy, apply
\autoref{thm:trie-key-path-exhaustion} and
\autoref{thm:trie-prefix-branch-determinacy}. The key-path theorem fixes the
finite prefix positions, and the branch theorem fixes the recorded left or
right subprefix at each displayed position.

For transport, apply \autoref{thm:trie-carrier-stability}. The same $\hsame$
and $\Cont$ routes move the visible rows without adding host string equality,
host maps, or unbounded trees. Lookup payload reads are then projected through
\autoref{thm:trie-lookup-payload-projection}.

For ledger exactness, apply \autoref{thm:trie-ledger-coverage}. Every
downstream read is a projection from the finite tuple $(k,v,l,b,p)$, so the
NameCert obligation surface is exhausted by the listed rows.
\end{proof}
