\begin{theorem}[IntUp dyadic mantissa real route]
\label{thm:int-dyadic-mantissa-real-route}
Every Real-and-Completion read of an $\IntUp$ signed-pair coordinate used as a
$\DyadicRatCoreUp$ mantissa first factors through
\autoref{ch:concrete-instances-nat-namecert},
\autoref{ch:concrete-instances-add-namecert},
\autoref{ch:concrete-instances-rat-namecert}, and
\autoref{ch:concrete-instances-dyadicratcore-namecert} before any
$\RealUp$ seal route is read. The route exports the signed-pair mantissa as a
BEDC lattice row, not as host integer equality, quotient representatives,
primitive subtraction, or ambient real completeness.
\end{theorem}
\begin{proof}
Start with the signed-pair additive lattice dependency of
\autoref{thm:int-signed-pair-additive-lattice-dependency}. It makes the
integer coordinate a Nat-and-Add balanced signed pair and gives the rational
side a signed numerator row rather than an independent integer quotient.

Next route that numerator through the existing rational and dyadic mantissa
surfaces. The rational row supplies the denominator-facing arithmetic context,
and the $\DyadicRatCoreUp$ row is the first place where the signed coordinate
is read as a dyadic mantissa for the Real-and-Completion chain.

Only after those four chapter surfaces have been crossed may a $\RealUp$ seal
consumer read the route. Since none of the preceding rows exports host integer
equality, quotient representatives, primitive subtraction, or ambient
completeness, the real-side read inherits only the displayed BEDC lattice
surface.
\end{proof}

\begin{theorem}[IntUp dyadic mantissa zero-sign normalization]
\label{thm:int-dyadic-mantissa-zero-sign-normalization}
Every Real-and-Completion read that uses an $\IntUp$ signed-pair coordinate as
the mantissa input of a $\DyadicRatCoreUp$ packet must first apply the
$\IntUp$ zero-sign boundary. Thus the two written zero rows determine the same
finite signed-mantissa source before $\RatUp$ denominator normalization and
$\DyadicRatCoreUp$ mantissa routing are read. The normalization is a finite
source-row condition only; it does not assert host integer equality, quotient
rational representatives, primitive subtraction, selected limits, or
$\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the refined zero-sign boundary
\autoref{thm:int-zero-sign-refined-boundary}. It identifies the two signed-pair
zero presentations as the same $\IntUp$ boundary row before the coordinate is
exported to any rational or dyadic consumer.

Next apply the route theorem
\autoref{thm:int-dyadic-mantissa-real-route}. It places every such mantissa read
behind the $\NatUp$, $\AddUp$, $\RatUp$, and $\DyadicRatCoreUp$ surfaces, so the
zero-sign boundary is already part of the finite row that enters the dyadic
packet.

Finally use source uniqueness
\autoref{thm:int-dyadic-mantissa-l10-source-uniqueness} together with the
sibling denominator route
\autoref{thm:int-dyadicratcore-denominator-route-sibling-repair}. After the
zero rows have collapsed to the same signed-mantissa source, the denominator
normalization and dyadic routing cannot split them again. Downstream
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ consumers therefore see only the
normalized finite row, with none of the excluded host-level data added.
\end{proof}

\begin{theorem}[IntUp dyadic mantissa L10 source uniqueness]
\label{thm:int-dyadic-mantissa-l10-source-uniqueness}
Let two L10 Real-and-Completion reads expose an $\IntUp$ signed-pair coordinate
as the mantissa input of a $\DyadicRatCoreUp$ packet. Suppose both reads display
the same $\IntUp$ signed-pair row, the same $\RatUp$ denominator normalization
surface, and the same $\DyadicRatCoreUp$ mantissa/denominator packet before the
$\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ consumers read it. Then the two
reads determine the same finite BEDC source row for that signed mantissa
handoff. This uniqueness is a statement about the displayed BEDC packet only;
it does not assert host integer equality, quotient rational representatives,
primitive subtraction, selected limits, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply the route theorem \autoref{thm:int-dyadic-mantissa-real-route}. It forces
each read through the $\NatUp$, $\AddUp$, $\RatUp$, and $\DyadicRatCoreUp$
chapter surfaces before any Real-and-Completion consumer can inspect a seal
boundary.

Next use the sibling route
\autoref{thm:int-dyadicratcore-denominator-route-sibling-repair} and the L10
handoff \autoref{thm:int-dyadicratcore-l10-denominator-handoff}. These identify
the source of the dyadic packet as the displayed $\IntUp$ signed-pair row
together with the displayed $\RatUp$ denominator normalization surface and the
dyadic mantissa route.

Finally apply the scoped source boundary
\autoref{thm:dyadicratcore-scoped-source-boundary} and signed-exponent source
determinacy \autoref{thm:dyadic-rat-core-signed-exponent-source-determinacy}.
Those rows say that downstream $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$
consumers can read only the visible finite dyadic packet. Since the two reads
share that packet before the consumers act, they determine the same finite BEDC
source row and no excluded host-level datum can split it into two sources.
\end{proof}
