\begin{theorem}[Integer history classifier positive append context iff]
\label{thm:int-history-classifier-positive-append-context-iff}
For all $a,m,n:\mathsf{BHist}$, if $\mathsf{Unary}(a)$,
$\mathsf{Unary}(m)$, and $\mathsf{Unary}(n)$, then the public same-sign
integer history classifier is invariant under adding the same visible unary
prefix to both magnitudes:
$$
\mathsf{IntHistoryClassifier}(\Ezero(\mathsf{append}(a,m)),\Ezero(\mathsf{append}(a,n)))
\Longleftrightarrow
\mathsf{IntHistoryClassifier}(\Ezero(m),\Ezero(n)).
$$
The one-tag branch satisfies the parallel context law:
$$
\mathsf{IntHistoryClassifier}(\Eone(\mathsf{append}(a,m)),\Eone(\mathsf{append}(a,n)))
\Longleftrightarrow
\mathsf{IntHistoryClassifier}(\Eone(m),\Eone(n)).
$$
The ten-field fit is the following. The traditional target is signed-integer
equality under a common unary magnitude context. The BEDC source consists of
$\mathsf{IntHistoryClassifier}$, $\mathsf{Unary}$, $\mathsf{append}$,
$\hsame$, and append cancellation. The carrier is the public signed-history
carrier. The classifier is the same-tag public classifier. Stability is common
unary prefix invariance. The ledger records the common visible unary prefix.
The core theorem is this iff statement. Exactness is preservation and
reflection of same-tag classifier equality. The standard bridge is ordinary
signed unary equality under equal magnitude shifts. The status is
$\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Apply Theorem~\ref{thm:int-history-classifier-same-tag-readback} to the
$\Ezero$ endpoints. With the unary closure of
$\mathsf{append}(a,m)$ and $\mathsf{append}(a,n)$, the left side reads back to
$\hsame(\mathsf{append}(a,m),\mathsf{append}(a,n))$ together with the two
unary payload witnesses. The right side reads back to
$\mathsf{Unary}(m)\land\mathsf{Unary}(n)\land\hsame(m,n)$.

For the zero-tag reverse direction, use congruence of $\mathsf{append}(a,-)$
on $\hsame(m,n)$ and unary append closure for the two payloads. Repacking by
the same-tag readback theorem gives the classifier on
$\Ezero(\mathsf{append}(a,m))$ and $\Ezero(\mathsf{append}(a,n))$.

For the zero-tag forward direction, read back the left classifier to obtain
$\hsame(\mathsf{append}(a,m),\mathsf{append}(a,n))$. Left append cancellation
under the common unary prefix $a$ recovers $\hsame(m,n)$, and the original
unary assumptions supply the two payload witnesses. Repacking by same-tag
readback gives $\mathsf{IntHistoryClassifier}(\Ezero(m),\Ezero(n))$.

The one-tag branch repeats the same two moves after replacing $\Ezero$ by
$\Eone$. The readback criterion is unchanged on payloads, so append congruence
proves the reverse implication, and left append cancellation proves the
forward implication before repacking the public classifier.
\end{proof}

\leanchecked{BEDC.Derived.IntUp.IntHistoryClassifier\_positive\_append\_context\_iff}

\begin{theorem}[Integer history classifier hsame transport]
\label{thm:int-history-classifier-hsame-transport}
For all $h,k,h',k':\mathsf{BHist}$, the public integer history classifier is
stable under replacement of both endpoints by $\hsame$-equal representatives:
$$
\hsame(h,h')\to
\hsame(k,k')\to
\mathsf{IntHistoryClassifier}(h,k)\to
\mathsf{IntHistoryClassifier}(h',k').
$$
The ten-field fit is the following. The traditional target is signed-integer
equality stable under representative replacement. The BEDC source consists of
$\mathsf{BHist}$, $\hsame$, $\Ezero$, $\Eone$, and
$\mathsf{IntHistoryClassifier}$. The carrier is
$\mathsf{IntHistoryCarrier}$. The classifier is the two-branch public
classifier. The stability endpoint is $\hsame$ transport. The ledger records
the visible sign tag together with the unary payload. The core theorem is this
transport statement. Exactness preservation is preservation of the classifier
under representative replacement. The standard bridge is replacement of
signed-unary representatives. The status is $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Unfold the classifier witness for $\mathsf{IntHistoryClassifier}(h,k)$ and
split its visible signed branch.

In the zero-tag branch, keep the unary payload witnesses $m,n$, the payload
comparison $\hsame(m,n)$, and the stored mixed-tag exclusion. Compose the old
endpoint witness $\hsame(h,\Ezero(m))$ with the symmetry of $\hsame(h,h')$ to
obtain $\hsame(h',\Ezero(m))$. The same composition with $\hsame(k,k')$ gives
$\hsame(k',\Ezero(n))$.

It remains to rebuild the branch exclusion at the transported endpoints. Given
a hypothetical one-tag witness from $h'$ and $k'$, compose it back through
$\hsame(h,h')$ and $\hsame(k,k')$ to obtain the corresponding one-tag witness
from $h$ and $k$. The stored zero-branch exclusion then rules it out, so the
zero-tag classifier branch repacks at $h'$ and $k'$.

In the one-tag branch, keep the same unary payload data and payload
comparison. The supplied endpoint transports compose with the old witnesses to
produce $\hsame(h',\Eone(m))$ and $\hsame(k',\Eone(n))$.

For the transported exclusion, any zero-tag witness at $h'$ and $k'$ composes
back to a zero-tag witness at $h$ and $k$. The stored one-branch exclusion
rules it out, and the one-tag classifier branch repacks with the original
payload witnesses.
\end{proof}

\begin{theorem}[IntUp mature signed-unary downstream package]
\label{thm:intup-mature-signed-unary-downstream-package}
The carrier $\mathsf{IntHistoryCarrier}$, the classifier
$\mathsf{IntHistoryClassifier}$, the same-tag readback iff, the positive
append-context iff, $\hsame$ transport, the canonical pair/history bridge, the
zero-sign refined boundary, and the integer signed-unary standard bridge
together form the mature signed-unary $\IntUp$ package consumed by $\RatUp$
numerator readback and by later ordered-ring or divisibility consumers. This
package imports no host $\mathsf{Nat}$, host equality,
quotient-normalization primitive, Euclidean division, or full ordered-ring API.
\end{theorem}
\begin{proof}
The public carrier and classifier are supplied by
\autoref{thm:concrete-int-history-semantic-namecert}. Their same-tag semantic
readback is \autoref{thm:int-history-classifier-same-tag-readback}, and the
common positive context law is
\autoref{thm:int-history-classifier-positive-append-context-iff}.

Representative stability is exactly
\autoref{thm:int-history-classifier-hsame-transport}. The external
pair/history interface is supplied by
\autoref{thm:int-canonical-difference-pair-history-bridge}, while
\autoref{thm:int-zero-sign-refined-boundary} isolates the refined zero-sign
boundary used by consumers that inspect signs.

Finally, \autoref{thm:int-signed-unary-standard-bridge} binds these classifier
and transport facts to the signed-unary standard bridge. The listed ingredients
therefore provide the public $\IntUp$ package used by $\RatUp$ numerator
readback and by later algebraic consumers. None of the cited facts introduces
a host $\mathsf{Nat}$ equality principle, quotient normalization, Euclidean
division, divisibility theory, or a full ordered-ring API.
\end{proof}
