\begin{theorem}[IntUp Nat Add Rat sibling route]
\label{thm:int-nat-add-rat-sibling-route}
Every signed-pair $\IntUp$ carrier route consumed by a later rational embedding
first reads the $\NatUp$ unary rows of
\autoref{ch:concrete-instances-nat-namecert}, the $\AddUp$ balance rows of
\autoref{ch:concrete-instances-add-namecert}, and the $\RatUp$ denominator
sibling rows of \autoref{ch:concrete-instances-rat-namecert}. The rational
consumer receives the displayed signed-pair carrier, additive balancing route,
and denominator packet; it receives no host integer quotient, primitive
subtraction operation, or field-level rational equality from the integer
boundary.
\end{theorem}
\begin{proof}
Read the signed-pair carrier from the integer interface. Its magnitude
coordinates are unary histories, so the route begins at the Nat certificate
surface, and its balance comparison is routed through the Add continuation
ledger.

Apply \autoref{thm:int-signed-pair-additive-lattice-dependency} and
\autoref{thm:int-rat-denominator-dependency-surface}. They identify the
integer row consumed by the rational side as the already displayed signed-pair
packet together with its additive balance rows.

Finally use \autoref{thm:int-rat-additive-denominator-route}. The $\RatUp$
consumer reads that balanced signed row beside the positive denominator
witness, so the sibling route is exactly Nat unary data, Add balance data, and
Rat denominator data. No step exports a host integer quotient or primitive
subtraction row.
\end{proof}

\begin{theorem}[IntUp Nat Add Rat Dyadic lattice readback]
\label{thm:int-nat-add-rat-dyadic-lattice-readback}
Every $\DyadicRatCoreUp$ signed-mantissa consumer of the $\IntUp$ surface first
factors through \autoref{ch:concrete-instances-nat-namecert},
\autoref{ch:concrete-instances-add-namecert},
\autoref{ch:concrete-instances-rat-namecert}, and then
\autoref{ch:concrete-instances-dyadicratcore-namecert}. The consumer receives
signed-unary branch data, $\AddUp$ balance rows, $\RatUp$ denominator rows, and
dyadic tolerance ledgers; it receives no host integer quotient, host rational
quotient, selected real limit, or $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:int-nat-add-rat-sibling-route}. It identifies the integer
surface consumed by rational embedding as a displayed signed-pair carrier whose
magnitude rows are read through $\NatUp$, whose balance rows are read through
$\AddUp$, and whose denominator-facing route is read through $\RatUp$.

Next apply \autoref{thm:dyadic-rat-core-rat-int-sibling-route}. The
$\DyadicRatCoreUp$ carrier reads its signed mantissa through the consumed
$\RatUp$ row and its sign and integer provenance through the consumed
$\IntUp$ row, while the exponent and denominator ledger stay visible as unary
history data.

Finally use \autoref{thm:dyadicratcore-l10-sibling-dependency-totality}. The
L10 dyadic-rational boundary exports exactly the finite dyadic tolerance ledger
read by the downstream faces. Since that dependency surface carries no host
rational quotient, selected real limit, or $\RealUp$ completeness theorem, and
the integer route already excludes host integer quotients, every
signed-mantissa consumer factors through the displayed Nat, Add, Rat, and
DyadicRatCore rows.
\end{proof}
