\begin{theorem}[Int signed numerator route into Rat]
\label{thm:int-rat-signed-numerator-route}
Every positive-denominator $\RatUp$ packet that consumes the $\IntUp$ surface reads signed numerator data only through the displayed signed numerator row, the $\NatUp$ magnitude row, the $\AddUp$ balancing row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row. The route may then pair that numerator with the positive denominator surface of \autoref{ch:concrete-instances-rat-namecert}, but it exports no host integer equality, quotient class of integer pairs, primitive subtraction row, or ambient field equality.
\end{theorem}
\begin{proof}
Start with the integer surface. The $\IntUp$ carrier presents the sign and magnitude of the numerator as finite signed-pair data, and the magnitude coordinate is read through the unary $\NatUp$ rows of \autoref{ch:concrete-instances-nat-namecert}.

The balancing evidence is routed through \autoref{ch:concrete-instances-add-namecert}. Thus a rational consumer sees the numerator only after the signed row and additive balancing row have both appeared in the same finite history packet.

The structural rows preserve that route componentwise. The $\hsame$ row transports the signed numerator, magnitude, and balancing coordinates; the $\Cont$ row replays the same displayed route; $\Pkg$ records the provenance; and the local $\NameCert$ row closes the accepted integer surface.

Finally the $\RatUp$ carrier of \autoref{ch:concrete-instances-rat-namecert} pairs that accepted numerator with a positive denominator row. Since neither the integer surface nor the rational pairing row contains host integer equality, quotient classes, primitive subtraction, or ambient field equality, no such data are exported by the dependency.
\end{proof}
