\begin{theorem}[Int sibling lattice pointer]
\label{thm:int-sibling-lattice-pointer}
Every Real-and-Completion consumer of the $\IntUp$ signed-pair surface,
including the $\DyadicRatCoreUp$ mantissa route of
\autoref{ch:concrete-instances-dyadicratcore-namecert} and the $\RatUp$
denominator routes of \autoref{ch:concrete-instances-rat-namecert}, reads
$\IntUp$ only through the displayed $\NatUp$ unary magnitude rows of
\autoref{ch:concrete-instances-nat-namecert}, the $\AddUp$
continuation-compatible balancing rows of
\autoref{ch:concrete-instances-add-namecert}, the $\RatUp$
signed-denominator consumer rows, and the local $\IntUp$ $\NameCert$ rows.
This lattice admits no host integer equality, quotient representative,
primitive subtraction, field-level rational equality at the $\IntUp$ boundary,
or ambient $\RealUp$ completeness operation.
\end{theorem}
\begin{proof}
Start with the local signed-pair surface. The sibling lattice of
\autoref{prop:int-nat-add-rat-sibling-dependency-lattice} places every
$\IntUp$ magnitude coordinate under the unary rows of
\autoref{ch:concrete-instances-nat-namecert} and every balancing comparison
under the continuation-compatible additive rows of
\autoref{ch:concrete-instances-add-namecert}. Thus the integer packet reaches
its signed-pair form through displayed Nat and Add data, not through a host
integer primitive.

Next read the rational consumer boundary. The signed-denominator dependency
\autoref{lem:int-rat-signed-denominator-dependency} and the additive
denominator route \autoref{thm:int-rat-additive-denominator-route} force a
$\RatUp$ consumer to take the balanced signed numerator beside the positive
denominator row of \autoref{ch:concrete-instances-rat-namecert}. Hence the
Rat-facing route can consume the local $\IntUp$ $\NameCert$ rows only after
the Nat and Add rows have already been displayed.

Finally pass to the dyadic and completion-facing consumers. The
$\DyadicRatCoreUp$ chapter \autoref{ch:concrete-instances-dyadicratcore-namecert}
names the $\IntUp$ and $\RatUp$ source certificates in its mantissa and
denominator ledger, so a Real-and-Completion reader reaches the integer source
only through that same finite route. None of the listed downstream consumers
has a coordinate for host integer equality, quotient representatives,
primitive subtraction, field-level rational equality at the $\IntUp$ boundary,
or ambient $\RealUp$ completeness, so those objects cannot be imported by this
sibling lattice pointer.
\end{proof}
