\begin{theorem}[$\BoolUp$ finite-data hub sibling route]
\label{thm:bool-finite-data-hub-sibling-route}
The $\BoolUp$ endpoint rows feed $\OptionUp$ constructor disjointness and $\ProdUp$ component projections through the same finite-data lattice. The $\OptionUp$ route of \autoref{ch:concrete-instances-option-namecert} reads the two endpoint rows as absent and present branch discriminators, while the $\ProdUp$ route of \autoref{ch:concrete-instances-prod-namecert} reads them as finite component selectors for product projections. Both consumers receive only the displayed $\BoolUp$ endpoint classifier, componentwise transport, replay, provenance, and local naming surface; neither receives host booleans, external equality, option payload data, product coordinate data, or product-pair equality from the $\BoolUp$ packet.
\end{theorem}
\begin{proof}
Project the finite-data lattice already displayed by the $\BoolUp$ carrier. Its available rows are the two endpoint histories, the endpoint classifier, componentwise transport, continuation replay, provenance, and local naming certificate.

The $\OptionUp$ sibling consumes only the endpoint distinction needed to separate absent and present constructors. Payload rows, nullable payload classifiers, and option equality remain owned by the option packet named in \autoref{ch:concrete-instances-option-namecert}.

The $\ProdUp$ sibling consumes the same finite distinction only as a component-facing selector. Product coordinate carriers, projection rows, and pair equality remain owned by the product packet named in \autoref{ch:concrete-instances-prod-namecert}.

Thus the hub-level sibling route exports a finite dependency edge from $\BoolUp$ to both consumers without adding any non-Boolean payload, product structure, host equality, or external Boolean principle to the $\BoolUp$ packet.
\end{proof}
