\begin{theorem}[$\BoolUp$ option-product sibling lattice link]
\label{thm:bool-option-prod-sibling-lattice-link}
The $\BoolUp$ finite truth classifier supplies the binary discriminator row consumed by $\OptionUp$ constructor disjointness in \autoref{ch:concrete-instances-option-namecert} and by $\ProdUp$ pair-envelope selection in \autoref{ch:concrete-instances-prod-namecert}. Both consumers read $\BoolUp$ only through the displayed two-endpoint truth classifier, componentwise transport, replay, provenance, and local naming rows. Neither consumer adds host booleans, external equality, option payload carriers, product coordinate carriers, or product-pair equality to the $\BoolUp$ packet.
\end{theorem}
\begin{proof}
Project the finite truth surface already displayed by the $\BoolUp$ carrier. The visible data are the two endpoint histories, their classifier row, and the structural rows that transport and replay that finite distinction.

The $\OptionUp$ consumer reads the two endpoints as absent and present branch markers before any payload row is inspected. The payload carrier and nullable payload classifier remain owned by the option chapter, so constructor disjointness imports only the binary discriminator.

The $\ProdUp$ consumer may read the same finite distinction only when a product envelope asks for a Boolean-facing coordinate or selector row. The pair carrier, coordinate carriers, and pair-envelope equality remain owned by the product chapter.

Thus both sibling routes consume the displayed $\BoolUp$ truth classifier without manufacturing host booleans or external equality. The exported dependency edge is the finite two-endpoint classifier and nothing stronger.
\end{proof}
