\begin{theorem}[PicardContraction metric complete Lipschitz consumer route]
\label{thm:picardcontraction-metric-complete-lipschitz-consumer-route}
Let $P=(B,T,L,I,M,E,H,C,G,N)$ be an accepted $\PicardContractionUp$ packet. Every $\OdeUp$, $\NewtonIterationUp$, $\RegSeqRatUp$, or $\RealUp$ consumer of $P$ reads the $\BanachUp$ source row through \autoref{ch:concrete-instances-banach-namecert}, the $\CompleteMetricUp$ boundary through \autoref{ch:concrete-instances-completemetric-namecert}, the contraction and Lipschitz rows through \autoref{ch:concrete-instances-lipschitzmap-namecert}, and the Cauchy-modulus row $M$ before the endpoint seal $E$.

Thus the consumer route is the finite dependency route
$$
B,T,L,I,M,E,H,C,G,N
$$
with the Banach, complete-metric, Lipschitz, and Cauchy-modulus rows visible before the endpoint seal. It does not export a host fixed point, completed orbit, ambient completeness theorem, selected limit, quotient stream equality, or external real-equality witness.
\end{theorem}
\begin{proof}
Project the packet $P$. The carrier rows are the Banach source $B$, contraction-map row $T$, rational Lipschitz ledger $L$, finite iterate ledger $I$, Cauchy-modulus row $M$, endpoint seal $E$, componentwise transport $H$, displayed continuation $C$, provenance $G$, and local naming row $N$.

Use the existing finite route theorems. The finite-iterate theorem \autoref{thm:picardcontraction-finite-iterate-closure} keeps iteration inside the displayed Banach and contraction rows, \autoref{thm:picardcontraction-banach-ode-boundary} routes ODE and Newton consumers through the Banach source and Lipschitz ledgers, and \autoref{thm:picardcontraction-cauchy-modulus-sibling-route} places the Cauchy-modulus row before the endpoint seal.

Now read the sibling boundaries. The Banach source is the packet row cited through \autoref{ch:concrete-instances-banach-namecert}; the complete-metric boundary is the finite convergence boundary of \autoref{ch:concrete-instances-completemetric-namecert}; and the contraction and modulus ledgers are the LipschitzMap rows of \autoref{ch:concrete-instances-lipschitzmap-namecert}.

It remains to inspect the excluded coordinates. None of $B,T,L,I,M,E,H,C,G,N$ is a host fixed point, completed orbit, ambient completeness theorem, selected limit, quotient stream equality, or external real-equality witness. Hence every listed downstream consumer receives only the displayed metric, complete, Lipschitz, and modulus route before the endpoint seal.
\end{proof}
