\chapter{Finite-Kernel Theorem Dependency DAG}
\label{ch:theorem-dependency-dag}

This chapter gives the proof dependency order for the finite-kernel sprint. It is a planning artifact for the proof target, not a new object-theory primitive.

\section{Milestone DAG}

The dependency chain is:
\[
\begin{array}{c}
\text{A. Mark layer}\\[2pt]
\downarrow\\[-2pt]
\text{B. History layer}\\[2pt]
\downarrow\\[-2pt]
\text{C. Extension and continuation}\\[2pt]
\downarrow\\[-2pt]
\text{D. Asking and signature generation}\\[2pt]
\downarrow\\[-2pt]
\text{E. Signature sameness}\\[2pt]
\downarrow\\[-2pt]
\text{F. Package policy}\\[2pt]
\downarrow\\[-2pt]
\text{G. Gap policy}\\[2pt]
\downarrow\\[-2pt]
\text{H. Composite ledger}\\[2pt]
\downarrow\\[-2pt]
\text{I. Naming certificates}
\end{array}
\]

The proof effort should not attempt large derived interfaces before Milestones A--G are mechanically checked.

\section{Milestone A: marks}

\begin{enumerate}
  \item \(\msame\)-reflexivity.
  \item \(\msame\)-symmetry.
  \item \(\msame\)-transitivity.
  \item Mark no-confusion: \(\bzero\) is not internally the same as \(\bone\), and conversely.
\end{enumerate}

\section{Milestone B: histories}

\begin{enumerate}
  \item \(\hsame\)-reflexivity.
  \item \(\hsame\)-symmetry.
  \item \(\hsame\)-transitivity.
  \item History no-confusion for empty, \(\Ezero\), and \(\Eone\) constructors.
\end{enumerate}

\section{Milestone C: relational extension and continuation}

\begin{enumerate}
  \item \(\ExtR\)-determinacy up to \(\hsame\).
  \label{thm:proof-sprint-extension-determinacy}
  \leanchecked{BEDC.FKernel.Ext.proof\_sprint\_extension\_determinacy}
  \item \(\ExtR\)-respect for \(\msame\) and \(\hsame\).
  \item \(\ContR\)-determinacy up to \(\hsame\).
  \item Left and right unit laws for \(\ContR\).
  \label{thm:proof-sprint-continuation-right-unit}
  \leanchecked{BEDC.FKernel.Cont.cont\_right\_unit\_proof\_sprint}
  \item Associativity of \(\ContR\) up to \(\hsame\).
\end{enumerate}

\section{Milestone D: asking and signatures}

\begin{enumerate}
  \item Generated bundle grammar is fixed.
  \item Signature generation rules are fixed.
  \item Under \(\AskPol(\Pi,D)\), signatures exist for histories in the domain.
  \item Under \(\AskPol(\Pi,D)\), signatures are deterministic up to \(\hsame\).
\end{enumerate}

\section{Milestone E: signature sameness}

\begin{enumerate}
  \item \(\sameSig\)-reflexivity under \(\AskPol\).
  \item \(\sameSig\)-symmetry.
  \item \(\sameSig\)-transitivity under deterministic signatures.
  \item Signature sameness is an equivalence relation on the chosen domain.
\end{enumerate}

\section{Milestones F--G: packages and gaps}

\begin{enumerate}
  \item \(\PkgPol\) existence.
  \item \(\PkgPol\) extensionality: internally same signatures yield internally same packages.
  \item \(\PkgPol\) grounding: internally same packages are justified by internally same signatures.
  \item \(\GapPol\) coverage: every admissible source history appears in some gap.
  \item \(\GapPol\) separation: genuinely different packages have disjoint source membership.
  \item Packaging classifies by signatures.
\end{enumerate}

\section{Milestone H: composite gap}

For two compression interfaces \(C\) and \(D\), prove:
\begin{enumerate}
  \item composite gap is defined by an intermediate witness;
  \item composite coverage follows from coverage of both stages;
  \item composite separation requires separation plus a suitable grounding condition.
\end{enumerate}

\section{Milestone I: naming certificates}

The first mechanically useful certificates should be:
\begin{enumerate}
  \item a unary repetition source certificate for \(\NatUp\);
  \item a continuation stability certificate for \(\AddUp\);
  \item a descent certificate for function-like interfaces;
  \item a ledger policy stating what is preserved by each derived name.
\end{enumerate}

\section{Execution rule}

The implementation sprint should stop at the first unverified milestone and not skip ahead. If Milestone A fails, later milestone statements are not repaired by changing the core theory silently; the affected definitions must be amended in place per the policy in Chapter~\ref{ch:theory-amendment-policy}.
