\begin{theorem}[QuantumStateUp observable measurement input boundary]
\label{thm:quantumstate-observable-measurement-input-boundary}
An $\ObservableUp$ expectation row may consume a $\QuantumStateUp$ input only
through the Hilbert row $\mathcal{H}$, the projective endpoint $p$, the
phase classifier $\phi$, the norm-one ledger $n$, the package provenance
$\rho$, and the displayed $\hsame/\Cont$ transport rows exported by
\autoref{thm:quantumstate-namecert-obligation-surface}. The expectation row
cannot inspect host vector equality, an ambient quotient object, or a phase
witness except through the $\QuantumStateUp$ classifier used to compare the
projective endpoint.
\end{theorem}
\begin{proof}
The observable expectation source is the row $E$ in
\autoref{def:observable-bhist-operator-carrier}. By
\autoref{thm:observable-quantumstate-expectation-boundary}, that row is read
through $\NameCert_{\QuantumStateUp}$ and is transported only by the displayed
classifier ledger of the observable packet.

Now read the public surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. Its exported state
input rows are exactly the Hilbert source $\mathcal{H}$, the projective
endpoint $p$, the phase classifier $\phi$, the norm-one ledger $n$, the
provenance row $\rho$, and the $\hsame/\Cont$ transport rows attached to
those fields.

The exclusion clauses follow from exactness of the same surface. Host vector
equality is not a field of \autoref{def:quantumstate-bhist-carrier}, quotient
equality is replaced by the projective classifier, and hidden phase data are
visible only through the classifier row. Thus an observable measurement input
has precisely the displayed $\mathsf{BHist}$ boundary.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix pure-state boundary]
\label{thm:quantumstate-densitymatrix-pure-state-boundary}
Any $\DensityMatrixUp$ pure-state row sourced from a $\QuantumStateUp$ carrier
packet must factor through the projective endpoint $p$ and the norm-one ledger
$n$ of that packet. The hidden phase data of the source state are visible only
through the $\QuantumStateUp$ phase classifier $\phi$ and projective classifier
$\lambda_P$, and no mixed-state ledger, affine-mixture spine, trace-class
classifier, spectral row, or channel row is imported back into the
$\QuantumStateUp$ carrier.
\end{theorem}
\begin{proof}
Use \autoref{thm:quantumstate-projective-phase-classifier} to identify the
source pure state by its unit Hilbert endpoint and projective endpoint rather
than by host vector equality. The norm side is fixed by
\autoref{thm:quantumstate-global-phase-stability}: $\hsame$ transport of the
Hilbert and projective rows preserves the phase classifier and the norm-one
ledger.

A density-matrix row then reads only the target density obligations. The
carrier and ledger clauses of \autoref{thm:densitymatrix-carrier-obligation}
and \autoref{thm:densitymatrix-positivity-trace-ledger-obligation} describe
trace-class membership, positivity, trace one, and the restricted
trace-class comparison on the density side.

Those density rows are consumer rows, not source-state fields. The public
$\QuantumStateUp$ surface of
\autoref{thm:quantumstate-namecert-obligation-surface} contains no
density-matrix row or affine-mixture ledger, so the only source information
available to a pure-state density row is the projective endpoint together
with the norm-one and phase-classifier data already carried by
$\QuantumStateUp$.
\end{proof}

\begin{theorem}[QuantumStateUp quantum-channel pure input boundary]
\label{thm:quantumstate-quantumchannel-pure-input-boundary}
$\QuantumChannelUp$ may act on a $\QuantumStateUp$ pure input only after the
associated density or projective input row has been read through the same
public $\QuantumStateUp$ surface described in
\autoref{thm:quantumstate-namecert-obligation-surface}. The channel output is
a density-matrix endpoint produced by the channel carrier and density-image
rows; it does not identify source states by host Hilbert-vector equality or by
any equality outside the $\QuantumStateUp$ projective classifier and the
density-matrix classifier it consumes.
\end{theorem}
\begin{proof}
First pass the pure input through the two preceding boundaries. The observable
boundary fixes the permitted $\QuantumStateUp$ input rows, while the
density-matrix pure-state boundary says that a density input sourced from a
pure state factors through the projective endpoint and norm-one ledger.

Now apply the channel surface. By \autoref{def:quantumchannel-cptp-carrier},
a channel acts on trace-class density endpoints, and
\autoref{lem:quantumchannel-densitymatrix-image} sends carried density inputs
to carried density outputs. For finite density mixtures,
\autoref{thm:quantumchannel-density-finite-mixture-preservation} preserves the
density affine-spine rows without opening the source state carrier.

Therefore a channel may read the pure input only after it has been presented
as the permitted density or projective input row. The output comparison lives
in the density-matrix and channel ledgers, while source-state comparison
remains the $\QuantumStateUp$ projective classifier transported through
$\hsame/\Cont$ rows.
\end{proof}

\begin{theorem}[Observable expectation readback]
\label{thm:quantumstate-observable-expectation-readback}
Every expectation row in an $\ObservableUp$ packet that consumes a
$\NameCert_{\QuantumStateUp}$ state input is read from a displayed
$\mathsf{BHist}$ and $\NameCert$ packet consisting only of the Hilbert source
row $\mathcal{H}$, the projective endpoint row $p$, the global-phase
classifier $\phi$, the norm ledger $n$, and the provenance row $\rho$ of
\autoref{def:quantumstate-bhist-carrier}. The observable expectation site may
pair those rows with the observable endpoint rows of
\autoref{ch:concrete-instances-observable-namecert}, but it receives no host
Hilbert-vector equality, no quotient object, and no density-matrix or channel
row from $\NameCert_{\QuantumStateUp}$.
\end{theorem}
\begin{proof}
The downstream observable input is the expectation-source row named in
\autoref{ch:concrete-instances-observable-namecert}. Read its state component
through the public $\NameCert_{\QuantumStateUp}$ surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. That surface exposes
exactly the carrier packet of \autoref{def:quantumstate-bhist-carrier}, the
projective classifier, the norm ledger, and the provenance row.

Now apply \autoref{thm:quantumstate-projective-consumer-boundary}. It gives
the complete consumer frontier for $\ObservableUp$: expectation evaluation may
use the Hilbert source row, projective endpoint, phase classifier, norm ledger,
and provenance. The observable endpoint itself is supplied by the observable
chapter, so no extra state equality, quotient representative, density row, or
channel row is imported from the state certificate.
\end{proof}

\begin{theorem}[DensityMatrix pure-state readback]
\label{thm:quantumstate-densitymatrix-pure-state-readback}
Every pure-state density row assembled by $\DensityMatrixUp$ from a
$\NameCert_{\QuantumStateUp}$ input is assembled only from the same displayed
unit-vector, projective-phase, norm, and provenance packet of
\autoref{def:quantumstate-bhist-carrier}, together with the density-matrix
carrier boundary of \autoref{ch:concrete-instances-densitymatrix-namecert}.
The readback does not expose a host vector equality, a quotient representative,
or a spectral decomposition as an additional state-side input.
\end{theorem}
\begin{proof}
The source packet is the $\QuantumStateUp$ carrier of
\autoref{def:quantumstate-bhist-carrier}. Its public certificate surface is
fixed by \autoref{thm:quantumstate-namecert-obligation-surface}: the available
state rows are the Hilbert source, projective endpoint, phase classifier, norm
ledger, and provenance rows, with hidden phase data readable only through the
classifier.

The density-matrix side supplies its own trace-class, positivity, and
trace-one carrier rows in
\autoref{ch:concrete-instances-densitymatrix-namecert}. Combining that carrier
boundary with \autoref{thm:quantumstate-projective-consumer-boundary} leaves
only the unit-vector/projective-phase packet as the state-side readback. Thus
the pure-state density row is assembled from the certified state packet plus
the density carrier boundary, not from host vector equality, quotient
representatives, or spectral data.
\end{proof}

\begin{theorem}[QuantumChannel input readback]
\label{thm:quantumstate-quantumchannel-input-readback}
A $\QuantumChannelUp$ input may consume a $\NameCert_{\QuantumStateUp}$ packet
only through the certified density and expectation boundary determined by
\autoref{def:quantumstate-bhist-carrier},
\autoref{thm:quantumstate-namecert-obligation-surface}, and
\autoref{thm:quantumstate-projective-consumer-boundary}. Its channel-side
rows in \autoref{ch:concrete-instances-quantumchannel-namecert} may refer to
the state only through those certified readbacks; they may not appeal to host
Hilbert-vector equality, quotient equality, or an unrecorded representative.
\end{theorem}
\begin{proof}
The channel input is downstream of the density-matrix and observable
interfaces named in \autoref{ch:concrete-instances-densitymatrix-namecert} and
\autoref{ch:concrete-instances-observable-namecert}. Those interfaces can read
the state only through the public rows of
\autoref{thm:quantumstate-namecert-obligation-surface}, namely the carrier
packet of \autoref{def:quantumstate-bhist-carrier} and its classifier,
ledger, and provenance rows.

Apply \autoref{thm:quantumstate-projective-consumer-boundary} at the
$\QuantumChannelUp$ site of
\autoref{ch:concrete-instances-quantumchannel-namecert}. The certified
density and expectation readbacks exhaust the permitted state access. Since
host vector equality, quotient equality, and unrecorded representatives are
not rows of the public state packet, they cannot be consumed by the channel
input.
\end{proof}
