\chapter{A Concrete Naming Certificate for $\QuantumStateUp$}
\label{ch:concrete-instances-quantumstate-namecert}

The quantum-state interface $\QuantumStateUp$ packages a unit vector in a Hilbert space carrier together with the equivalence under global phase. It depends on $\NameCert_{\HilbertUp}$ (\autoref{ch:concrete-instances-hilbert-namecert}) and $\NameCert_{\ProjectiveSpaceUp}$ (\autoref{ch:concrete-instances-projectivespace-namecert}).

\section{Carrier definition}
\label{sec:quantumstate-carrier}

\begin{definition}[QuantumStateUp BHist carrier]
\label{def:quantumstate-bhist-carrier}
A $\QuantumStateUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho).
$$
The row $\mathcal{H}$ is a consumed $\NameCert_{\HilbertUp}$ row. The row
$\mathcal{P}$ is a consumed $\NameCert_{\ProjectiveSpaceUp}$ row over the
displayed projective line determined by $\mathcal{H}$. The endpoint $v$ is the
unit-vector row projected from $\mathcal{H}$, $n$ is the norm-one ledger row,
$\phi$ is the global-phase row, and $p$ is the projective-line endpoint row
projected from $\mathcal{P}$.

The rows $\lambda_H$ and $\lambda_P$ are the inherited Hilbert and projective
classifier rows, respectively. The row $\rho$ is the $\mathsf{Pkg}$ provenance
record witnessing that the two consumed certificates and all displayed endpoint
rows belong to the same finite packet. No carrier datum outside
$\mathcal{H}$, $\mathcal{P}$, $v$, $n$, $\phi$, $p$, $\lambda_H$, $\lambda_P$,
and $\rho$ is part of the public $\QuantumStateUp$ row.
\end{definition}

\section{The certificate}
\label{sec:quantumstate-certificate}

\begin{theorem}[QuantumStateUp Hilbert source boundary]
\label{thm:quantumstate-hilbert-source-boundary}
For every carrier packet $\mathcal{Q}$ of
\autoref{def:quantumstate-bhist-carrier}, all vector, norm, and inner-product
rows used by the $\QuantumStateUp$ interface are projected from the consumed
$\NameCert_{\HilbertUp}$ row $\mathcal{H}$. In particular, the visible vector
endpoint $v$, the norm-one ledger $n$, and every inner-product row used to test
unit length are read through $\mathcal{H}$ and the inherited classifier
$\lambda_H$, not through an ambient Hilbert-space carrier.
\end{theorem}
\begin{proof}
The traditional target is a Hilbert-space unit vector carrying the usual norm
and inner-product data. The BEDC source is the consumed
$\NameCert_{\HilbertUp}$ row $\mathcal{H}$, and the carrier choice is the finite
packet $\mathcal{Q}$ of \autoref{def:quantumstate-bhist-carrier}.

Unpack the definition of $\mathcal{Q}$. The only fields naming Hilbert-side
data are $\mathcal{H}$, $v$, $n$, and $\lambda_H$, together with the provenance
row $\rho$. Thus the classifier choice is the inherited Hilbert classifier
$\lambda_H$, stability is $\hsame$ transport through that classifier, and the
ledger is the norm-one row $n$.

The core theorem list for this boundary consists of the visible endpoint
projection, the norm-one ledger projection, and the inner-product projection.
Exactness says that every Hilbert-side row visible to $\QuantumStateUp$ is one
of those projected rows. There is no standard bridge supplied here, and the
status is a paper obligation for the $\NameCert_{\QuantumStateUp}$ Hilbert
source boundary.
\end{proof}

\begin{theorem}[QuantumStateUp projective phase classifier]
\label{thm:quantumstate-projective-phase-classifier}
The classified $\QuantumStateUp$ rows are exactly the Hilbert unit-vector rows
$v$ whose projective endpoints $p$ are related by the global-phase row $\phi$
and the $\ProjectiveSpaceUp$ classifier $\lambda_P$. Equivalently, two carrier
packets
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
and
$$
\mathcal{Q}'=(\mathcal{H}',\mathcal{P}',v',n',\phi',p',\lambda'_H,\lambda'_P,\rho')
$$
classify the same quantum state precisely when the Hilbert endpoint rows are
unit-vector rows and the projective endpoints are identified by the displayed
global-phase/projective-space classifier rows. The classifier records no host
vector equality, no independent Hilbert-space quotient, and no primitive
quotient object beyond the projective scaling classifier supplied by
$\mathcal{P}$.
\end{theorem}
\begin{proof}
The traditional target is equality of pure quantum states modulo global phase.
The BEDC source is the pair of consumed certificates
$\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$. The carrier
choice is the packet $\mathcal{Q}$, while the classifier choice is the pair
formed by the global-phase row $\phi$ and the projective classifier
$\lambda_P$.

For the forward reading, a classified $\QuantumStateUp$ row first exposes a
Hilbert endpoint $v$ and its norm-one ledger $n$ through
\autoref{thm:quantumstate-hilbert-source-boundary}. It then exposes the
projective endpoint $p$ through $\mathcal{P}$. The row $\phi$ records the
allowed phase change, and $\lambda_P$ records the projective classifier that
accepts the resulting endpoint comparison.

For the reverse reading, a Hilbert unit-vector endpoint with a norm-one ledger
and a projective endpoint accepted by $\phi$ and $\lambda_P$ supplies all fields
of \autoref{def:quantumstate-bhist-carrier}. Stability is componentwise
$\hsame$ transport through $\lambda_H$ and $\lambda_P$, the ledger is $n$
together with the phase row $\phi$, and exactness says that no host quotient is
read. The core theorem list is this classifier row together with the Hilbert
source boundary. The standard bridge is absent, and the status is a paper
obligation for the $\NameCert_{\QuantumStateUp}$ classifier.
\end{proof}

\begin{theorem}[QuantumStateUp global phase stability]
\label{thm:quantumstate-global-phase-stability}
Let $\mathcal{Q}$ and $\mathcal{Q}'$ be two carrier packets of
\autoref{def:quantumstate-bhist-carrier}. If the Hilbert rows
$\mathcal{H},v,n,\lambda_H$ and the projective rows
$\mathcal{P},p,\lambda_P$ are transported componentwise by $\hsame$, then the
global-phase classifier row is preserved and the norm-one ledger remains a
valid $\QuantumStateUp$ ledger row. Thus $\hsame$ transport of the consumed
Hilbert and projective certificates preserves the phase classifier and the
norm-one condition.
\end{theorem}
\begin{proof}
The traditional target is invariance of a pure state under change of certified
presentation. The BEDC source is the pair of source certificates
$\mathcal{H}$ and $\mathcal{P}$, the carrier choice is the packet
$\mathcal{Q}$, and the classifier choice is $\lambda_H$, $\lambda_P$, and the
phase row $\phi$.

Transport the Hilbert side first. The $\hsame$ witnesses for
$\mathcal{H}$, $v$, $n$, and $\lambda_H$ move the unit-vector endpoint and the
norm-one ledger through the Hilbert classifier without opening any host vector
equality.

Transport the projective side next. The $\hsame$ witnesses for
$\mathcal{P}$, $p$, and $\lambda_P$ move the projective endpoint and its
classifier row. The phase row $\phi$ is preserved because its source and target
endpoints are exactly the transported Hilbert and projective endpoints.

The ledger consists of the norm-one row, the phase row, and the provenance
row. The core theorem list is the Hilbert source boundary, the projective phase
classifier, and this transport row. Exactness says that every preserved row is
one of the displayed packet fields. No standard bridge is supplied, and the
status is a paper obligation for $\NameCert_{\QuantumStateUp}$ stability.
\end{proof}

\begin{theorem}[QuantumStateUp public obligation surface]
\label{thm:quantumstate-namecert-obligation-surface}
The public $\NameCert_{\QuantumStateUp}$ surface consists exactly of the
carrier packet of \autoref{def:quantumstate-bhist-carrier}, the projective
phase classifier of \autoref{thm:quantumstate-projective-phase-classifier}, the
stability row of \autoref{thm:quantumstate-global-phase-stability}, the
norm-one ledger, the projective exactness predicate, and the hidden
global-phase rows needed to witness the endpoint comparison. These rows form
the carrier, classifier, stability, ledger, exactness, and hidden
global-phase obligations exported by $\QuantumStateUp$. The surface contains
no density-matrix row, measurement row, channel row, or spectral row.
\end{theorem}
\begin{proof}
The traditional target is the pure-state naming certificate. The BEDC source
is the pair $\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$, and
the carrier choice is the displayed packet $\mathcal{Q}$. The classifier choice
is the global-phase/projective classifier, while stability is
\autoref{thm:quantumstate-global-phase-stability}.

The ledger is finite: it contains the norm-one row $n$, the phase row $\phi$,
the two inherited classifier rows $\lambda_H$ and $\lambda_P$, and the
provenance row $\rho$. The core theorem list is the Hilbert source boundary,
the projective phase classifier, and the global-phase stability row.

Exactness says that every public $\QuantumStateUp$ row is assembled from those
fields and that every hidden phase row is used only to classify projective
endpoints. The named dependency certificates expose no density-matrix,
measurement, channel, or spectral row at this site. The standard bridge field
is empty. The status is a paper obligation for the $\NameCert_{\QuantumStateUp}$
public surface.
\end{proof}

\begin{theorem}[QuantumStateUp observable measurement input boundary]
\label{thm:quantumstate-observable-measurement-input-boundary}
An $\ObservableUp$ expectation row may consume a $\QuantumStateUp$ input only
through the Hilbert row $\mathcal{H}$, the projective endpoint $p$, the
phase classifier $\phi$, the norm-one ledger $n$, the package provenance
$\rho$, and the displayed $\hsame/\Cont$ transport rows exported by
\autoref{thm:quantumstate-namecert-obligation-surface}. The expectation row
cannot inspect host vector equality, an ambient quotient object, or a phase
witness except through the $\QuantumStateUp$ classifier used to compare the
projective endpoint.
\end{theorem}
\begin{proof}
The observable expectation source is the row $E$ in
\autoref{def:observable-bhist-operator-carrier}. By
\autoref{thm:observable-quantumstate-expectation-boundary}, that row is read
through $\NameCert_{\QuantumStateUp}$ and is transported only by the displayed
classifier ledger of the observable packet.

Now read the public surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. Its exported state
input rows are exactly the Hilbert source $\mathcal{H}$, the projective
endpoint $p$, the phase classifier $\phi$, the norm-one ledger $n$, the
provenance row $\rho$, and the $\hsame/\Cont$ transport rows attached to
those fields.

The exclusion clauses follow from exactness of the same surface. Host vector
equality is not a field of \autoref{def:quantumstate-bhist-carrier}, quotient
equality is replaced by the projective classifier, and hidden phase data are
visible only through the classifier row. Thus an observable measurement input
has precisely the displayed $\mathsf{BHist}$ boundary.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix pure-state boundary]
\label{thm:quantumstate-densitymatrix-pure-state-boundary}
Any $\DensityMatrixUp$ pure-state row sourced from a $\QuantumStateUp$ carrier
packet must factor through the projective endpoint $p$ and the norm-one ledger
$n$ of that packet. The hidden phase data of the source state are visible only
through the $\QuantumStateUp$ phase classifier $\phi$ and projective classifier
$\lambda_P$, and no mixed-state ledger, affine-mixture spine, trace-class
classifier, spectral row, or channel row is imported back into the
$\QuantumStateUp$ carrier.
\end{theorem}
\begin{proof}
Use \autoref{thm:quantumstate-projective-phase-classifier} to identify the
source pure state by its unit Hilbert endpoint and projective endpoint rather
than by host vector equality. The norm side is fixed by
\autoref{thm:quantumstate-global-phase-stability}: $\hsame$ transport of the
Hilbert and projective rows preserves the phase classifier and the norm-one
ledger.

A density-matrix row then reads only the target density obligations. The
carrier and ledger clauses of \autoref{thm:densitymatrix-carrier-obligation}
and \autoref{thm:densitymatrix-positivity-trace-ledger-obligation} describe
trace-class membership, positivity, trace one, and the restricted
trace-class comparison on the density side.

Those density rows are consumer rows, not source-state fields. The public
$\QuantumStateUp$ surface of
\autoref{thm:quantumstate-namecert-obligation-surface} contains no
density-matrix row or affine-mixture ledger, so the only source information
available to a pure-state density row is the projective endpoint together
with the norm-one and phase-classifier data already carried by
$\QuantumStateUp$.
\end{proof}

\begin{theorem}[QuantumStateUp quantum-channel pure input boundary]
\label{thm:quantumstate-quantumchannel-pure-input-boundary}
$\QuantumChannelUp$ may act on a $\QuantumStateUp$ pure input only after the
associated density or projective input row has been read through the same
public $\QuantumStateUp$ surface described in
\autoref{thm:quantumstate-namecert-obligation-surface}. The channel output is
a density-matrix endpoint produced by the channel carrier and density-image
rows; it does not identify source states by host Hilbert-vector equality or by
any equality outside the $\QuantumStateUp$ projective classifier and the
density-matrix classifier it consumes.
\end{theorem}
\begin{proof}
First pass the pure input through the two preceding boundaries. The observable
boundary fixes the permitted $\QuantumStateUp$ input rows, while the
density-matrix pure-state boundary says that a density input sourced from a
pure state factors through the projective endpoint and norm-one ledger.

Now apply the channel surface. By \autoref{def:quantumchannel-cptp-carrier},
a channel acts on trace-class density endpoints, and
\autoref{lem:quantumchannel-densitymatrix-image} sends carried density inputs
to carried density outputs. For finite density mixtures,
\autoref{thm:quantumchannel-density-finite-mixture-preservation} preserves the
density affine-spine rows without opening the source state carrier.

Therefore a channel may read the pure input only after it has been presented
as the permitted density or projective input row. The output comparison lives
in the density-matrix and channel ledgers, while source-state comparison
remains the $\QuantumStateUp$ projective classifier transported through
$\hsame/\Cont$ rows.
\end{proof}

\begin{theorem}[Observable expectation readback]
\label{thm:quantumstate-observable-expectation-readback}
Every expectation row in an $\ObservableUp$ packet that consumes a
$\NameCert_{\QuantumStateUp}$ state input is read from a displayed
$\mathsf{BHist}$ and $\NameCert$ packet consisting only of the Hilbert source
row $\mathcal{H}$, the projective endpoint row $p$, the global-phase
classifier $\phi$, the norm ledger $n$, and the provenance row $\rho$ of
\autoref{def:quantumstate-bhist-carrier}. The observable expectation site may
pair those rows with the observable endpoint rows of
\autoref{ch:concrete-instances-observable-namecert}, but it receives no host
Hilbert-vector equality, no quotient object, and no density-matrix or channel
row from $\NameCert_{\QuantumStateUp}$.
\end{theorem}
\begin{proof}
The downstream observable input is the expectation-source row named in
\autoref{ch:concrete-instances-observable-namecert}. Read its state component
through the public $\NameCert_{\QuantumStateUp}$ surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. That surface exposes
exactly the carrier packet of \autoref{def:quantumstate-bhist-carrier}, the
projective classifier, the norm ledger, and the provenance row.

Now apply \autoref{thm:quantumstate-projective-consumer-boundary}. It gives
the complete consumer frontier for $\ObservableUp$: expectation evaluation may
use the Hilbert source row, projective endpoint, phase classifier, norm ledger,
and provenance. The observable endpoint itself is supplied by the observable
chapter, so no extra state equality, quotient representative, density row, or
channel row is imported from the state certificate.
\end{proof}

\begin{theorem}[DensityMatrix pure-state readback]
\label{thm:quantumstate-densitymatrix-pure-state-readback}
Every pure-state density row assembled by $\DensityMatrixUp$ from a
$\NameCert_{\QuantumStateUp}$ input is assembled only from the same displayed
unit-vector, projective-phase, norm, and provenance packet of
\autoref{def:quantumstate-bhist-carrier}, together with the density-matrix
carrier boundary of \autoref{ch:concrete-instances-densitymatrix-namecert}.
The readback does not expose a host vector equality, a quotient representative,
or a spectral decomposition as an additional state-side input.
\end{theorem}
\begin{proof}
The source packet is the $\QuantumStateUp$ carrier of
\autoref{def:quantumstate-bhist-carrier}. Its public certificate surface is
fixed by \autoref{thm:quantumstate-namecert-obligation-surface}: the available
state rows are the Hilbert source, projective endpoint, phase classifier, norm
ledger, and provenance rows, with hidden phase data readable only through the
classifier.

The density-matrix side supplies its own trace-class, positivity, and
trace-one carrier rows in
\autoref{ch:concrete-instances-densitymatrix-namecert}. Combining that carrier
boundary with \autoref{thm:quantumstate-projective-consumer-boundary} leaves
only the unit-vector/projective-phase packet as the state-side readback. Thus
the pure-state density row is assembled from the certified state packet plus
the density carrier boundary, not from host vector equality, quotient
representatives, or spectral data.
\end{proof}

\begin{theorem}[QuantumChannel input readback]
\label{thm:quantumstate-quantumchannel-input-readback}
A $\QuantumChannelUp$ input may consume a $\NameCert_{\QuantumStateUp}$ packet
only through the certified density and expectation boundary determined by
\autoref{def:quantumstate-bhist-carrier},
\autoref{thm:quantumstate-namecert-obligation-surface}, and
\autoref{thm:quantumstate-projective-consumer-boundary}. Its channel-side
rows in \autoref{ch:concrete-instances-quantumchannel-namecert} may refer to
the state only through those certified readbacks; they may not appeal to host
Hilbert-vector equality, quotient equality, or an unrecorded representative.
\end{theorem}
\begin{proof}
The channel input is downstream of the density-matrix and observable
interfaces named in \autoref{ch:concrete-instances-densitymatrix-namecert} and
\autoref{ch:concrete-instances-observable-namecert}. Those interfaces can read
the state only through the public rows of
\autoref{thm:quantumstate-namecert-obligation-surface}, namely the carrier
packet of \autoref{def:quantumstate-bhist-carrier} and its classifier,
ledger, and provenance rows.

Apply \autoref{thm:quantumstate-projective-consumer-boundary} at the
$\QuantumChannelUp$ site of
\autoref{ch:concrete-instances-quantumchannel-namecert}. The certified
density and expectation readbacks exhaust the permitted state access. Since
host vector equality, quotient equality, and unrecorded representatives are
not rows of the public state packet, they cannot be consumed by the channel
input.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix readback boundary]
\label{thm:quantumstate-densitymatrix-readback-boundary}
A $\DensityMatrixUp$ consumer that reads back a rank-one density row from a
public $\NameCert_{\QuantumStateUp}$ packet may read only the Hilbert source
row $\mathcal{H}$, the projective endpoint row $p$, the norm ledger $n$, the
phase classifier $\phi$, and the package provenance $\rho$ exported by
\autoref{def:quantumstate-bhist-carrier}. Any rank-one density row sourced
from the state must factor through the projective classifier of
\autoref{thm:quantumstate-projective-phase-classifier}; it may not use host
Hilbert-vector equality as a public input.
\end{theorem}
\begin{proof}
Project the state packet $\mathcal{Q}$ through
\autoref{def:quantumstate-bhist-carrier}. The readable rows are exactly the
Hilbert source, projective endpoint, norm ledger, phase classifier, and
provenance fields already exposed by
\autoref{thm:quantumstate-namecert-obligation-surface}.

The rank-one readback step is then forced through the projective classifier.
Apply \autoref{thm:quantumstate-projective-phase-classifier} to convert the
hidden phase witness into the public endpoint comparison, and use
\autoref{thm:quantumstate-global-phase-stability} to keep that comparison
stable under the same classified packet.

Finally, package the allowed rows through $\mathsf{BHist}$, $\Cont$,
$\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance. No density row adds a
host vector equality: the only equality available to the consumer is the
projective classifier row exported by the public surface.
\end{proof}

\begin{theorem}[QuantumStateUp observable expectation source]
\label{thm:quantumstate-observable-expectation-source}
An $\ObservableUp$ expectation row sourced from a public
$\NameCert_{\QuantumStateUp}$ packet uses the observable packet together with
exactly the $\QuantumStateUp$ Hilbert source row $\mathcal{H}$ and projective
endpoint row $p$. The phase witness remains hidden behind the classifier
$\phi$, and the expectation source may read no host vector equality,
density-matrix row, measurement outcome row, or ambient function-space
equality from $\QuantumStateUp$.
\end{theorem}
\begin{proof}
Begin with the observable packet and the public state packet $\mathcal{Q}$.
The state side contributes only the Hilbert and projective rows displayed in
\autoref{def:quantumstate-bhist-carrier}, together with the norm ledger and
provenance fields named by
\autoref{thm:quantumstate-namecert-obligation-surface}.

The phase data is not passed as a separate witness. Use
\autoref{thm:quantumstate-projective-phase-classifier} to expose only the
classified endpoint row, and use
\autoref{thm:quantumstate-global-phase-stability} to show that the observable
source is insensitive to changing representatives inside the same classified
state packet.

The expectation source is therefore repackaged through $\mathsf{BHist}$,
$\Cont$, $\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance using only those
rows. Since no other $\QuantumStateUp$ field is projected, no density,
measurement, or ambient function-space equality is introduced.
\end{proof}

\begin{theorem}[QuantumStateUp channel input exactness]
\label{thm:quantumstate-channel-input-exactness}
$\QuantumChannelUp$ input transport is exact for the public
$\NameCert_{\QuantumStateUp}$ packet. A classified input packet exposes the
same Hilbert source row $\mathcal{H}$, projective endpoint row $p$, norm ledger
$n$, phase row $\phi$, and package provenance $\rho$ as the source packet, and
it adds no density-matrix row, measurement row, or ambient function-space
equality.
\end{theorem}
\begin{proof}
Project the source packet through
\autoref{def:quantumstate-bhist-carrier}. The transported input is classified
by the same public rows: Hilbert source, projective endpoint, norm ledger,
phase classifier, and provenance.

Exactness follows by using
\autoref{thm:quantumstate-namecert-obligation-surface} as the complete list of
exported state rows. Apply
\autoref{thm:quantumstate-projective-phase-classifier} to keep the projective
endpoint as the channel-visible state classifier, and apply
\autoref{thm:quantumstate-global-phase-stability} to preserve the phase row
under classified transport.

The channel input is then repacked through $\mathsf{BHist}$, $\Cont$,
$\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance. Because the repacking
uses only the displayed packet fields, the input surface is exact and no
density-matrix, measurement, or ambient function-space equality is added.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix consumer exclusion]
\label{thm:quantumstate-densitymatrix-consumer-exclusion}
A $\DensityMatrixUp$ consumer of $\NameCert_{\QuantumStateUp}$ may read only the
Hilbert source row $\mathcal{H}$, the projective endpoint row $p$, the
global-phase classifier $\phi$, the norm ledger $n$, and the package provenance
$\rho$ from the pure-state certificate. The trace-class row, positivity row, and
trace-one row required for a density matrix must be supplied by
$\DensityMatrixUp$ itself. They are not fields of the finite $\mathsf{BHist}$
packet $\mathcal{Q}$ and are not consequences of the pure-state package
provenance alone.
\end{theorem}
\begin{proof}
Unpack the carrier packet of \autoref{def:quantumstate-bhist-carrier}. Its
public rows are $\mathcal{H}$, $\mathcal{P}$, $v$, $n$, $\phi$, $p$,
$\lambda_H$, $\lambda_P$, and $\rho$, with the consumer-readable boundary
restricted by \autoref{thm:quantumstate-projective-consumer-boundary}.

Compare this finite list with the public obligation surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. The only rows exported
to a downstream construction are the Hilbert source, projective endpoint, phase
classifier, norm ledger, and provenance rows. None of the displayed fields is a
trace-class carrier, a positivity witness, or a trace-one ledger.

Thus a $\DensityMatrixUp$ construction may use the pure-state certificate as its
input boundary, but its density rows must enter through its own $\mathsf{BHist}$
packet and $\mathsf{Pkg}$ provenance. Reading those rows from
$\NameCert_{\QuantumStateUp}$ would require a field absent from the carrier and
from the obligation surface.
\end{proof}

\begin{theorem}[QuantumStateUp observable measurement readback boundary]
\label{thm:quantumstate-observable-measurement-readback-boundary}
An $\ObservableUp$ measurement readback over a $\QuantumStateUp$ input factors
through the Hilbert classifier row $\lambda_H$ and the projective phase
classifier formed by $\phi$ and $\lambda_P$. The outcome row, spectral row, and
observable package provenance are supplied by $\ObservableUp$ rather than by the
state certificate, and cannot be read as hidden rows of
$\NameCert_{\QuantumStateUp}$.
\end{theorem}
\begin{proof}
Project the consumer-readable rows described in
\autoref{thm:quantumstate-projective-consumer-boundary}. The state input gives a
Hilbert source row, a projective endpoint row, a phase classifier, a norm ledger,
and the package provenance for the pure-state packet.

Measurement readback uses these rows only to classify the input state. The
Hilbert part is read through $\lambda_H$, while the projective part is read
through $\phi$ and $\lambda_P$ as in
\autoref{thm:quantumstate-projective-phase-classifier}.

The observable rows have different provenance. Outcome and spectral data are
introduced by the observable packet and its own $\mathsf{Pkg}$ row, so they are
separate from the $\mathsf{BHist}$ fields listed in
\autoref{def:quantumstate-bhist-carrier}. Therefore the readback boundary
factors through the state classifiers and leaves observable output rows to
$\ObservableUp$.
\end{proof}

\begin{theorem}[QuantumStateUp channel phase-classifier preservation]
\label{thm:quantumstate-channel-phase-classifier-preservation}
A $\QuantumChannelUp$ consumer transporting a pure-state input by $\hsame$ and
$\Cont$ ledgers must preserve the displayed projective phase classifier of
$\NameCert_{\QuantumStateUp}$. It may repack the Hilbert source, projective
endpoint, phase classifier, norm ledger, and provenance rows as its channel
input boundary, but it may not replace the phase classifier by host vector
equality or by equality in an ambient quotient object.
\end{theorem}
\begin{proof}
Start with the $\hsame$ transport row of
\autoref{thm:quantumstate-global-phase-stability}. It preserves the Hilbert
source rows, the projective endpoint rows, the norm-one ledger, and the
global-phase classifier through the displayed carrier fields.

The classifier being preserved is the one characterized by
\autoref{thm:quantumstate-projective-phase-classifier}. That theorem identifies
the public comparison with the projective endpoint row and the phase classifier,
not with host Hilbert-vector equality and not with an ambient quotient equality.

Finally, repack the allowed rows using
\autoref{thm:quantumstate-projective-consumer-boundary}. The channel side may
attach its own $\Cont$ ledger to transport the input boundary, but the incoming
phase row remains the displayed $\QuantumStateUp$ classifier. Any replacement by
host equality would add a row absent from the carrier packet and from the public
obligation surface.
\end{proof}

