\begin{theorem}[QuantumStateUp phase ledger exhaustion]
\label{thm:quantumstate-phase-ledger-exhaustion}
Every hidden row used to classify two $\QuantumStateUp$ carrier packets is
one of the displayed phase row $\phi$, inherited Hilbert classifier
$\lambda_H$, inherited projective classifier $\lambda_P$, norm-one ledger
$n$, endpoint $\hsame$ transport row, or provenance row $\rho$ from the
carrier of \autoref{def:quantumstate-bhist-carrier}. Conversely, those
rows reconstruct exactly the projective phase classifier of
\autoref{thm:quantumstate-projective-phase-classifier} inside the consumed
$\NameCert_{\HilbertUp}$ and $\NameCert_{\ProjectiveSpaceUp}$ packets.
\end{theorem}
\begin{proof}
Start from two displayed packets
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
and
$$
\mathcal{Q}'=(\mathcal{H}',\mathcal{P}',v',n',\phi',p',\lambda'_H,\lambda'_P,\rho').
$$
The carrier definition lists the only rows available to the classifier.
Thus a hidden classifier row must be read from the phase row, one of the
inherited classifiers, the norm ledger, the endpoint $\hsame$ transport
data, or the $\mathsf{Pkg}$ provenance record.

For exhaustion, use \autoref{thm:quantumstate-namecert-obligation-surface}
to identify the public $\NameCert_{\QuantumStateUp}$ obligations and
\autoref{thm:quantumstate-projective-consumer-boundary} to rule out
consumer access to a stronger equality. The stability row in
\autoref{thm:quantumstate-global-phase-stability} accounts for every
endpoint transport through $\hsame$, while the provenance exactness of
\autoref{thm:quantumstate-provenance-row-exactness} keeps those transports
inside the same finite $\mathsf{BHist}$ package.

For reconstruction, read the Hilbert endpoint through $\lambda_H$, read the
norm ledger through $n$, and read the projective endpoint comparison through
$\phi$ and $\lambda_P$. These are precisely the inputs named by
\autoref{thm:quantumstate-projective-phase-classifier}; repacking them with
$\rho$ recovers the same projective phase classifier and adds no hidden
row beyond the displayed ledger.
\end{proof}

\begin{theorem}[QuantumStateUp consumer readback completeness]
\label{thm:quantumstate-consumer-readback-completeness}
Every downstream $\ObservableUp$, $\DensityMatrixUp$, and
$\QuantumChannelUp$ consumer row reading $\NameCert_{\QuantumStateUp}$
factors through the five public fields named in
\autoref{thm:quantumstate-projective-consumer-boundary}: the Hilbert source
row $\mathcal{H}$, projective endpoint row $p$, global-phase classifier
$\phi$, norm ledger $n$, and package provenance $\rho$. Conversely, any
consumer depending only on those five fields is stable under
\autoref{thm:quantumstate-global-phase-stability}.
\end{theorem}
\begin{proof}
The forward direction is a readback claim. By
\autoref{def:quantumstate-bhist-carrier}, a consumer begins with a finite
$\mathsf{BHist}$ packet carried by $\mathsf{Pkg}$ provenance. By
\autoref{thm:quantumstate-namecert-obligation-surface}, the public
$\NameCert_{\QuantumStateUp}$ surface supplies the carrier, classifier,
stability, ledger, exactness, and hidden phase obligations, but it supplies
no observable, density-matrix, channel, or spectral row.

Apply \autoref{thm:quantumstate-projective-consumer-boundary}. The rows
that remain readable by $\ObservableUp$, $\DensityMatrixUp$, and
$\QuantumChannelUp$ consumers are exactly $\mathcal{H}$, $p$, $\phi$, $n$,
and $\rho$. The projective classifier theorem
\autoref{thm:quantumstate-projective-phase-classifier} explains how the
endpoint and phase comparison behind those five fields is classified
without exposing host vector equality or a quotient primitive.

For the converse direction, suppose a consumer depends only on
$\mathcal{H}$, $p$, $\phi$, $n$, and $\rho$. Transport the Hilbert and
projective source data by the $\hsame$ rows governed by $\lambda_H$ and
$\lambda_P$. The global-phase stability theorem
\autoref{thm:quantumstate-global-phase-stability} preserves the phase row
and norm ledger, and \autoref{thm:quantumstate-provenance-row-exactness}
preserves the finite package boundary. Therefore the consumer readback is
unchanged under certified global-phase transport.
\end{proof}

\begin{theorem}[QuantumStateUp observable expectation input exactness]
\label{thm:quantumstate-observable-expectation-input-exactness}
An $\ObservableUp$ expectation consumer that receives
$\NameCert_{\QuantumStateUp}$ may read exactly the state rows
$\mathcal{H}$, $v$, $n$, $p$, $\phi$, $\lambda_H$, $\lambda_P$, and $\rho$
from the carrier packet of \autoref{def:quantumstate-bhist-carrier}. The
expectation input is the $\mathsf{BHist}$ endpoint $v$ scoped by the
Hilbert row $\mathcal{H}$, the norm-one ledger $n$, the projective endpoint
$p$, the global-phase row $\phi$, the inherited classifier rows
$\lambda_H$ and $\lambda_P$, and the $\mathsf{Pkg}$ provenance row $\rho$.
It may not read an observable spectrum row, measurement-result row,
host-level vector equality, or state data outside the displayed
$\NameCert_{\QuantumStateUp}$ classifier.
\end{theorem}
\begin{proof}
Unpack the carrier packet of \autoref{def:quantumstate-bhist-carrier}. The
rows available to any consumer are the two source certificates, the Hilbert
endpoint, the norm-one ledger, the phase and projective endpoint data, the
two inherited classifiers, and the finite provenance package. The observable
expectation site uses the state side of this packet, so its state input is
the listed eight rows
$$
\mathcal{H},v,n,p,\phi,\lambda_H,\lambda_P,\rho.
$$

The classifier is fixed by
\autoref{thm:quantumstate-projective-phase-classifier}. Thus $v$ is not read
as a raw host vector: it is read as a Hilbert $\mathsf{BHist}$ endpoint
whose admissible comparisons pass through $\lambda_H$, $\phi$, and
$\lambda_P$. The stability available to the expectation consumer is exactly
\autoref{thm:quantumstate-global-phase-stability}, so changing certified
presentations transports the same input rows by $\hsame$ rather than by a
host quotient.

Exactness follows from
\autoref{thm:quantumstate-namecert-obligation-surface} together with
\autoref{thm:quantumstate-projective-consumer-boundary}. The public surface
contains no spectral, measurement, density-matrix, or channel row, and the
consumer boundary forbids equality outside the Hilbert and projective
classifiers. Therefore the observable expectation input is precisely the
displayed $\mathsf{BHist}$ and $\mathsf{Pkg}$ row family.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix pure ray readback]
\label{thm:quantumstate-densitymatrix-pure-ray-readback}
A $\DensityMatrixUp$ pure-state consumer reading
$\NameCert_{\QuantumStateUp}$ may recover only the projective ray endpoint
$p$ together with the Hilbert source row $\mathcal{H}$, the endpoint row
$v$, the norm-one ledger $n$, the global-phase row $\phi$, the inherited
classifiers $\lambda_H,\lambda_P$, and the provenance row $\rho$. Its
readback is a certified pure ray in $\mathsf{BHist}/\hsame$ terms, not a
host vector quotient and not an already supplied density-matrix row.
\end{theorem}
\begin{proof}
Start with the carrier packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho).
$$
The pure-density consumer needs a ray source and a unit ledger. These are
already the projective endpoint $p$ and the norm-one Hilbert ledger $n$,
with $v$ serving only as the certified Hilbert endpoint from which the ray
row is projected.

Apply \autoref{thm:quantumstate-projective-phase-classifier} to identify the
ray comparison used by the consumer. The global-phase row $\phi$ and the
projective classifier $\lambda_P$ determine sameness of pure rays, while
$\lambda_H$ scopes the Hilbert endpoint and norm ledger. Apply
\autoref{thm:quantumstate-global-phase-stability} to transport this
readback along $\hsame$ without changing the rows that the consumer may
inspect.

The exclusion is the constructive content. By
\autoref{thm:quantumstate-namecert-obligation-surface}, no density-matrix row
is exported by $\NameCert_{\QuantumStateUp}$. By
\autoref{thm:quantumstate-projective-consumer-boundary}, no host vector
quotient or equality outside the displayed classifiers is available. Thus a
pure-state density-matrix consumer can build its downstream row only from
the certified ray endpoint, the norm-one Hilbert ledger, and the same
$\mathsf{Pkg}$ provenance record.
\end{proof}

\begin{theorem}[QuantumStateUp channel consumer input boundary]
\label{thm:quantumstate-channel-consumer-input-boundary}
A $\QuantumChannelUp$ state-input consumer of
$\NameCert_{\QuantumStateUp}$ is stable under the same
global-phase/projective classifier as $\QuantumStateUp$. Its input rows are
limited to $\mathcal{H}$, $v$, $n$, $p$, $\phi$, $\lambda_H$, $\lambda_P$,
and $\rho$ from the carrier packet; it carries no independent channel row,
no density-matrix row, and no classifier other than the inherited
$\mathsf{BHist}$, $\hsame$, $\mathsf{Pkg}$, and $\NameCert$ data already
exported by the state certificate.
\end{theorem}
\begin{proof}
Unpack \autoref{def:quantumstate-bhist-carrier} and read the state input as
a finite $\mathsf{BHist}$ package. The endpoint supplied to a channel is
$v$ together with its norm-one ledger $n$, its projective endpoint $p$, the
phase row $\phi$, the inherited classifiers $\lambda_H,\lambda_P$, and the
provenance row $\rho$ tying these rows to the consumed source certificates.

The classifier for this input is not chosen by the channel consumer. It is
the classifier of \autoref{thm:quantumstate-projective-phase-classifier}:
Hilbert endpoint transport is scoped by $\lambda_H$, and ray transport is
scoped by $\phi$ and $\lambda_P$. The stability required by the channel
input is exactly \autoref{thm:quantumstate-global-phase-stability}, which
keeps the same finite row family under componentwise $\hsame$ transport.

Finally apply \autoref{thm:quantumstate-namecert-obligation-surface} and
\autoref{thm:quantumstate-projective-consumer-boundary}. The public surface
exports no channel datum and no density-matrix datum, while the consumer
boundary forbids a separate quotient or host equality. Repacking the
displayed rows therefore gives the whole channel state-input boundary in
$\mathsf{BHist}/\hsame/\mathsf{Pkg}/\NameCert$ terms.
\end{proof}
