\begin{theorem}[Observable expectation readback]
\label{thm:quantumstate-observable-expectation-readback}
Every expectation row in an $\ObservableUp$ packet that consumes a
$\NameCert_{\QuantumStateUp}$ state input is read from a displayed
$\mathsf{BHist}$ and $\NameCert$ packet consisting only of the Hilbert source
row $\mathcal{H}$, the projective endpoint row $p$, the global-phase
classifier $\phi$, the norm ledger $n$, and the provenance row $\rho$ of
\autoref{def:quantumstate-bhist-carrier}. The observable expectation site may
pair those rows with the observable endpoint rows of
\autoref{ch:concrete-instances-observable-namecert}, but it receives no host
Hilbert-vector equality, no quotient object, and no density-matrix or channel
row from $\NameCert_{\QuantumStateUp}$.
\end{theorem}
\begin{proof}
The downstream observable input is the expectation-source row named in
\autoref{ch:concrete-instances-observable-namecert}. Read its state component
through the public $\NameCert_{\QuantumStateUp}$ surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. That surface exposes
exactly the carrier packet of \autoref{def:quantumstate-bhist-carrier}, the
projective classifier, the norm ledger, and the provenance row.

Now apply \autoref{thm:quantumstate-projective-consumer-boundary}. It gives
the complete consumer frontier for $\ObservableUp$: expectation evaluation may
use the Hilbert source row, projective endpoint, phase classifier, norm ledger,
and provenance. The observable endpoint itself is supplied by the observable
chapter, so no extra state equality, quotient representative, density row, or
channel row is imported from the state certificate.
\end{proof}

\begin{theorem}[DensityMatrix pure-state readback]
\label{thm:quantumstate-densitymatrix-pure-state-readback}
Every pure-state density row assembled by $\DensityMatrixUp$ from a
$\NameCert_{\QuantumStateUp}$ input is assembled only from the same displayed
unit-vector, projective-phase, norm, and provenance packet of
\autoref{def:quantumstate-bhist-carrier}, together with the density-matrix
carrier boundary of \autoref{ch:concrete-instances-densitymatrix-namecert}.
The readback does not expose a host vector equality, a quotient representative,
or a spectral decomposition as an additional state-side input.
\end{theorem}
\begin{proof}
The source packet is the $\QuantumStateUp$ carrier of
\autoref{def:quantumstate-bhist-carrier}. Its public certificate surface is
fixed by \autoref{thm:quantumstate-namecert-obligation-surface}: the available
state rows are the Hilbert source, projective endpoint, phase classifier, norm
ledger, and provenance rows, with hidden phase data readable only through the
classifier.

The density-matrix side supplies its own trace-class, positivity, and
trace-one carrier rows in
\autoref{ch:concrete-instances-densitymatrix-namecert}. Combining that carrier
boundary with \autoref{thm:quantumstate-projective-consumer-boundary} leaves
only the unit-vector/projective-phase packet as the state-side readback. Thus
the pure-state density row is assembled from the certified state packet plus
the density carrier boundary, not from host vector equality, quotient
representatives, or spectral data.
\end{proof}

\begin{theorem}[QuantumChannel input readback]
\label{thm:quantumstate-quantumchannel-input-readback}
A $\QuantumChannelUp$ input may consume a $\NameCert_{\QuantumStateUp}$ packet
only through the certified density and expectation boundary determined by
\autoref{def:quantumstate-bhist-carrier},
\autoref{thm:quantumstate-namecert-obligation-surface}, and
\autoref{thm:quantumstate-projective-consumer-boundary}. Its channel-side
rows in \autoref{ch:concrete-instances-quantumchannel-namecert} may refer to
the state only through those certified readbacks; they may not appeal to host
Hilbert-vector equality, quotient equality, or an unrecorded representative.
\end{theorem}
\begin{proof}
The channel input is downstream of the density-matrix and observable
interfaces named in \autoref{ch:concrete-instances-densitymatrix-namecert} and
\autoref{ch:concrete-instances-observable-namecert}. Those interfaces can read
the state only through the public rows of
\autoref{thm:quantumstate-namecert-obligation-surface}, namely the carrier
packet of \autoref{def:quantumstate-bhist-carrier} and its classifier,
ledger, and provenance rows.

Apply \autoref{thm:quantumstate-projective-consumer-boundary} at the
$\QuantumChannelUp$ site of
\autoref{ch:concrete-instances-quantumchannel-namecert}. The certified
density and expectation readbacks exhaust the permitted state access. Since
host vector equality, quotient equality, and unrecorded representatives are
not rows of the public state packet, they cannot be consumed by the channel
input.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix readback boundary]
\label{thm:quantumstate-densitymatrix-readback-boundary}
A $\DensityMatrixUp$ consumer that reads back a rank-one density row from a
public $\NameCert_{\QuantumStateUp}$ packet may read only the Hilbert source
row $\mathcal{H}$, the projective endpoint row $p$, the norm ledger $n$, the
phase classifier $\phi$, and the package provenance $\rho$ exported by
\autoref{def:quantumstate-bhist-carrier}. Any rank-one density row sourced
from the state must factor through the projective classifier of
\autoref{thm:quantumstate-projective-phase-classifier}; it may not use host
Hilbert-vector equality as a public input.
\end{theorem}
\begin{proof}
Project the state packet $\mathcal{Q}$ through
\autoref{def:quantumstate-bhist-carrier}. The readable rows are exactly the
Hilbert source, projective endpoint, norm ledger, phase classifier, and
provenance fields already exposed by
\autoref{thm:quantumstate-namecert-obligation-surface}.

The rank-one readback step is then forced through the projective classifier.
Apply \autoref{thm:quantumstate-projective-phase-classifier} to convert the
hidden phase witness into the public endpoint comparison, and use
\autoref{thm:quantumstate-global-phase-stability} to keep that comparison
stable under the same classified packet.

Finally, package the allowed rows through $\mathsf{BHist}$, $\Cont$,
$\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance. No density row adds a
host vector equality: the only equality available to the consumer is the
projective classifier row exported by the public surface.
\end{proof}

\begin{theorem}[QuantumStateUp observable expectation source]
\label{thm:quantumstate-observable-expectation-source}
An $\ObservableUp$ expectation row sourced from a public
$\NameCert_{\QuantumStateUp}$ packet uses the observable packet together with
exactly the $\QuantumStateUp$ Hilbert source row $\mathcal{H}$ and projective
endpoint row $p$. The phase witness remains hidden behind the classifier
$\phi$, and the expectation source may read no host vector equality,
density-matrix row, measurement outcome row, or ambient function-space
equality from $\QuantumStateUp$.
\end{theorem}
\begin{proof}
Begin with the observable packet and the public state packet $\mathcal{Q}$.
The state side contributes only the Hilbert and projective rows displayed in
\autoref{def:quantumstate-bhist-carrier}, together with the norm ledger and
provenance fields named by
\autoref{thm:quantumstate-namecert-obligation-surface}.

The phase data is not passed as a separate witness. Use
\autoref{thm:quantumstate-projective-phase-classifier} to expose only the
classified endpoint row, and use
\autoref{thm:quantumstate-global-phase-stability} to show that the observable
source is insensitive to changing representatives inside the same classified
state packet.

The expectation source is therefore repackaged through $\mathsf{BHist}$,
$\Cont$, $\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance using only those
rows. Since no other $\QuantumStateUp$ field is projected, no density,
measurement, or ambient function-space equality is introduced.
\end{proof}

\begin{theorem}[QuantumStateUp channel input exactness]
\label{thm:quantumstate-channel-input-exactness}
$\QuantumChannelUp$ input transport is exact for the public
$\NameCert_{\QuantumStateUp}$ packet. A classified input packet exposes the
same Hilbert source row $\mathcal{H}$, projective endpoint row $p$, norm ledger
$n$, phase row $\phi$, and package provenance $\rho$ as the source packet, and
it adds no density-matrix row, measurement row, or ambient function-space
equality.
\end{theorem}
\begin{proof}
Project the source packet through
\autoref{def:quantumstate-bhist-carrier}. The transported input is classified
by the same public rows: Hilbert source, projective endpoint, norm ledger,
phase classifier, and provenance.

Exactness follows by using
\autoref{thm:quantumstate-namecert-obligation-surface} as the complete list of
exported state rows. Apply
\autoref{thm:quantumstate-projective-phase-classifier} to keep the projective
endpoint as the channel-visible state classifier, and apply
\autoref{thm:quantumstate-global-phase-stability} to preserve the phase row
under classified transport.

The channel input is then repacked through $\mathsf{BHist}$, $\Cont$,
$\hsame$, $\mathsf{Pkg}$, and $\NameCert$ provenance. Because the repacking
uses only the displayed packet fields, the input surface is exact and no
density-matrix, measurement, or ambient function-space equality is added.
\end{proof}

\begin{theorem}[QuantumStateUp density-matrix consumer exclusion]
\label{thm:quantumstate-densitymatrix-consumer-exclusion}
A $\DensityMatrixUp$ consumer of $\NameCert_{\QuantumStateUp}$ may read only the
Hilbert source row $\mathcal{H}$, the projective endpoint row $p$, the
global-phase classifier $\phi$, the norm ledger $n$, and the package provenance
$\rho$ from the pure-state certificate. The trace-class row, positivity row, and
trace-one row required for a density matrix must be supplied by
$\DensityMatrixUp$ itself. They are not fields of the finite $\mathsf{BHist}$
packet $\mathcal{Q}$ and are not consequences of the pure-state package
provenance alone.
\end{theorem}
\begin{proof}
Unpack the carrier packet of \autoref{def:quantumstate-bhist-carrier}. Its
public rows are $\mathcal{H}$, $\mathcal{P}$, $v$, $n$, $\phi$, $p$,
$\lambda_H$, $\lambda_P$, and $\rho$, with the consumer-readable boundary
restricted by \autoref{thm:quantumstate-projective-consumer-boundary}.

Compare this finite list with the public obligation surface of
\autoref{thm:quantumstate-namecert-obligation-surface}. The only rows exported
to a downstream construction are the Hilbert source, projective endpoint, phase
classifier, norm ledger, and provenance rows. None of the displayed fields is a
trace-class carrier, a positivity witness, or a trace-one ledger.

Thus a $\DensityMatrixUp$ construction may use the pure-state certificate as its
input boundary, but its density rows must enter through its own $\mathsf{BHist}$
packet and $\mathsf{Pkg}$ provenance. Reading those rows from
$\NameCert_{\QuantumStateUp}$ would require a field absent from the carrier and
from the obligation surface.
\end{proof}

\begin{theorem}[QuantumStateUp observable measurement readback boundary]
\label{thm:quantumstate-observable-measurement-readback-boundary}
An $\ObservableUp$ measurement readback over a $\QuantumStateUp$ input factors
through the Hilbert classifier row $\lambda_H$ and the projective phase
classifier formed by $\phi$ and $\lambda_P$. The outcome row, spectral row, and
observable package provenance are supplied by $\ObservableUp$ rather than by the
state certificate, and cannot be read as hidden rows of
$\NameCert_{\QuantumStateUp}$.
\end{theorem}
\begin{proof}
Project the consumer-readable rows described in
\autoref{thm:quantumstate-projective-consumer-boundary}. The state input gives a
Hilbert source row, a projective endpoint row, a phase classifier, a norm ledger,
and the package provenance for the pure-state packet.

Measurement readback uses these rows only to classify the input state. The
Hilbert part is read through $\lambda_H$, while the projective part is read
through $\phi$ and $\lambda_P$ as in
\autoref{thm:quantumstate-projective-phase-classifier}.

The observable rows have different provenance. Outcome and spectral data are
introduced by the observable packet and its own $\mathsf{Pkg}$ row, so they are
separate from the $\mathsf{BHist}$ fields listed in
\autoref{def:quantumstate-bhist-carrier}. Therefore the readback boundary
factors through the state classifiers and leaves observable output rows to
$\ObservableUp$.
\end{proof}

\begin{theorem}[QuantumStateUp channel phase-classifier preservation]
\label{thm:quantumstate-channel-phase-classifier-preservation}
A $\QuantumChannelUp$ consumer transporting a pure-state input by $\hsame$ and
$\Cont$ ledgers must preserve the displayed projective phase classifier of
$\NameCert_{\QuantumStateUp}$. It may repack the Hilbert source, projective
endpoint, phase classifier, norm ledger, and provenance rows as its channel
input boundary, but it may not replace the phase classifier by host vector
equality or by equality in an ambient quotient object.
\end{theorem}
\begin{proof}
Start with the $\hsame$ transport row of
\autoref{thm:quantumstate-global-phase-stability}. It preserves the Hilbert
source rows, the projective endpoint rows, the norm-one ledger, and the
global-phase classifier through the displayed carrier fields.

The classifier being preserved is the one characterized by
\autoref{thm:quantumstate-projective-phase-classifier}. That theorem identifies
the public comparison with the projective endpoint row and the phase classifier,
not with host Hilbert-vector equality and not with an ambient quotient equality.

Finally, repack the allowed rows using
\autoref{thm:quantumstate-projective-consumer-boundary}. The channel side may
attach its own $\Cont$ ledger to transport the input boundary, but the incoming
phase row remains the displayed $\QuantumStateUp$ classifier. Any replacement by
host equality would add a row absent from the carrier packet and from the public
obligation surface.
\end{proof}

\begin{theorem}[QuantumStateUp provenance row exactness]
\label{thm:quantumstate-provenance-row-exactness}
For every carrier packet
$$
\mathcal{Q}=(\mathcal{H},\mathcal{P},v,n,\phi,p,\lambda_H,\lambda_P,\rho)
$$
of \autoref{def:quantumstate-bhist-carrier}, the provenance row $\rho$
partitions the public rows of $\mathcal{Q}$ exactly into the consumed
$\NameCert_{\HilbertUp}$ packet $\mathcal{H}$, the consumed
$\NameCert_{\ProjectiveSpaceUp}$ packet $\mathcal{P}$, the displayed
norm row $n$, phase row $\phi$, projective endpoint row $p$, Hilbert
endpoint row $v$, and inherited classifier rows $\lambda_H,\lambda_P$.
No observable row, density-matrix row, channel row, spectral row,
host-vector-equality row, or quotient row belongs to the public
$\mathsf{BHist}$ packet witnessed by $\rho$.
\end{theorem}
\begin{proof}
Use the carrier display in \autoref{def:quantumstate-bhist-carrier} as the
row inventory. The packet has the two consumed $\NameCert$ rows
$\mathcal{H}$ and $\mathcal{P}$, the endpoint and ledger rows
$v,n,\phi,p$, the inherited classifiers $\lambda_H,\lambda_P$, and the
provenance row $\rho$. The row $\rho$ is therefore the $\mathsf{Pkg}$
record tying exactly those rows into one finite $\mathsf{BHist}$ packet.

The Hilbert portion is supplied by
\autoref{thm:quantumstate-namecert-obligation-surface}: it exposes the
carrier, classifier, stability, ledger, exactness, and hidden phase rows
but no downstream observable object. The projective portion is supplied by
\autoref{thm:quantumstate-projective-phase-classifier}: it reads phase
classification through $\phi$ and $\lambda_P$, not through a host quotient.

Finally apply the consumer boundary in
\autoref{thm:quantumstate-projective-consumer-boundary}. A downstream row
may inspect only the named Hilbert, projective, phase, norm, and provenance
fields. Together with the global-phase stability theorem
\autoref{thm:quantumstate-global-phase-stability}, this proves that
$\rho$ is exact for the displayed $\NameCert$ package and excludes every
observable, density-matrix, channel, spectral, host-vector-equality, and
quotient row from the public surface.
\end{proof}
