\chapter{A Concrete Naming Certificate for $\BishopRealCompletionAdjointUp$}
\label{ch:concrete-instances-bishop-real-completion-adjoint-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopRealCompletionAdjointUp$ packet records the finite adjoint surface by which a Bishop regular real name is admitted into the completion route and read back through the same L10 data. It sits after the regular completion monad of \autoref{ch:concrete-instances-regular-cauchy-completion-monad-namecert}, the Cauchy completion functor of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, the universal property row of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the visible real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a non-quotient public completion-adjoint boundary; it does not assert ambient completeness of $\RealUp$, choose completed limits, compare host real values, or identify quotient streams.

\begin{definition}[Bishop real completion adjoint carrier]
\label{def:bishop-real-completion-adjoint-carrier}
A $\BishopRealCompletionAdjointUp$ carrier is a finite $\BHist$ packet
$$
A=(M,F,U,R,E,J,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\RegularCauchyCompletionMonadUp$ row, recording the finite unit and bind schedule for completion-facing regular names.
\item $F$ is the $\CauchyCompletionFunctorUp$ row, recording the source-to-completion transport used by functorial consumers.
\item $U$ is the $\CompletionUniversalPropertyUp$ row, recording extension existence and uniqueness only as displayed finite ledger data.
\item $R$ is the $\RegSeqRatUp$ readback row reached by the source windows and by the completion-facing unit request.
\item $E$ is the terminal $\RealUp$ seal row, visible only after $M,F,U,R$ have been read.
\item $J$ is the unit-extension handoff row, matching the unit row of $M$ with the extension row of $U$ through the functorial surface $F$.
\item $T$ is the triangle-ledger row, recording exactness for the unit leg, extension leg, readback leg, and Real seal leg.
\item $H$ records componentwise $\hsame$ transport for the monad, functor, universal-property, readback, seal, handoff, triangle-ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
M,F,U \longmapsto R \longmapsto E \longmapsto J,T,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\BishopRealCompletionAdjointUp$, $\RegularCauchyCompletionMonadUp$, $\CauchyCompletionFunctorUp$, $\CompletionUniversalPropertyUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopRealCompletionAdjointUp}$ row.
\end{enumerate}
The accepted carrier is exactly the displayed packet $A$. It has no coordinate for quotient completion equality, selected limits, host real equality, countable choice, ambient $\RealUp$ completeness, or a detached adjunction theorem outside the finite rows.
\end{definition}

\begin{theorem}[Bishop real completion adjoint NameCert obligations]
\label{thm:bishop-real-completion-adjoint-namecert-obligations}
For every accepted carrier $A=(M,F,U,R,E,J,T,H,C,P,N)$, the local $\NameCert_{\BishopRealCompletionAdjointUp}$ obligations are exhausted by carrier admission for the displayed monad, functor, universal-property, readback, seal, unit-extension handoff, triangle-ledger, transport, replay, provenance, and local naming rows. No obligation may call on quotient completion equality, a selected limit, host real equality, countable choice, ambient $\RealUp$ completeness, or an external adjunction principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-real-completion-adjoint-carrier}. The only rows visible to the local classifier are $M,F,U,R,E,J,T,H,C,P,N$.

Read the completion route in order. The monad row supplies the finite unit and bind schedule, the functor row supplies the completion-facing transport, and the universal-property row supplies the displayed extension ledger. Only after those rows are present may the readback row $R$ and terminal seal row $E$ be consumed.

The handoff and exactness rows are structural over that same route. The row $J$ compares the unit and extension legs, $T$ records the triangle ledger, $H$ transports displayed coordinates, $C$ replays the permitted reads, and $P,N$ record provenance and local naming. Since the carrier has no excluded coordinate, no local obligation can export one.
\end{proof}

\begin{theorem}[Bishop real completion adjoint unit-extension handoff]
\label{thm:bishop-real-completion-adjoint-unit-extension-handoff}
Let $A=(M,F,U,R,E,J,T,H,C,P,N)$ be an accepted $\BishopRealCompletionAdjointUp$ carrier. Every unit-extension read factors first through the $\RegularCauchyCompletionMonadUp$ unit row in $M$, then through the $\CauchyCompletionFunctorUp$ source-to-completion row $F$, and only then through the $\CompletionUniversalPropertyUp$ extension ledger $U$. The handoff row $J$ records this finite route before the $\RegSeqRatUp$ readback $R$ and terminal $\RealUp$ seal $E$ are exposed.
\end{theorem}
\begin{proof}
Start with the monad row. The unit part of $M$ admits source regular data into the completion interface through finite windows and tolerance rows.

Next apply the functor row $F$. It transports the same displayed source data to the completion-facing route without introducing a quotient completion object or selected representative.

Finally read the universal-property row $U$. The handoff row $J$ can compare unit and extension data only after $M$ and $F$ have been projected. The readback $R$, seal $E$, transport $H$, replay $C$, provenance $P$, and local naming $N$ preserve that order, so the consumer receives a finite handoff rather than a host adjunction.
\end{proof}

\begin{theorem}[Bishop real completion adjoint triangle ledger exactness]
\label{thm:bishop-real-completion-adjoint-triangle-ledger-exactness}
For every accepted $\BishopRealCompletionAdjointUp$ carrier $A=(M,F,U,R,E,J,T,H,C,P,N)$, the triangle-ledger row $T$ is exact for the displayed unit leg, extension leg, regular readback leg, and terminal Real seal leg. Any completion-facing consumer that reads the public adjoint surface must account for the rows
$$
M,F,U,R,E,J,T,H,C,P,N
$$
in that order, and it obtains no quotient stream equality, selected completion point, host real equality, countable-choice schedule, ambient completeness theorem, or detached adjunction proof.
\end{theorem}
\begin{proof}
Project the accepted carrier. The triangle ledger $T$ is not an independent theorem row; it is displayed beside the monad, functor, universal-property, readback, seal, and handoff rows.

Use the unit-extension handoff of \autoref{thm:bishop-real-completion-adjoint-unit-extension-handoff}. It places $J$ downstream of $M,F,U$ and upstream of $R,E$, so every triangle comparison is read through the same finite route.

The structural rows finish the ledger accounting. Componentwise transport in $H$ preserves the displayed coordinates, replay in $C$ records the allowed reads, and $P,N$ bind provenance and naming. Because the carrier contains no excluded row, exactness of $T$ remains a finite ledger statement and cannot become a quotient, choice, host-equality, completeness, or external-adjunction claim.
\end{proof}

\begin{closurestatus}{\BishopRealCompletionAdjointUp}
  \constructivestory{A $\BishopRealCompletionAdjointUp$ packet is generated from a regular completion monad row, a Cauchy completion functor row, a completion universal-property row, a RegSeqRat readback, a Real seal, unit-extension handoff, triangle-ledger exactness, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-real-completion-adjoint-carrier}, \autoref{thm:bishop-real-completion-adjoint-namecert-obligations}, \autoref{thm:bishop-real-completion-adjoint-unit-extension-handoff}, and \autoref{thm:bishop-real-completion-adjoint-triangle-ledger-exactness} seed the non-quotient completion-adjoint packet over the monad, functor, universal-property, readback, and Real seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completion equality, selected completed limits, host real equality, countable choice, ambient Real completeness, Lean verification, bridge checking, or a host adjunction theorem.}
  \upgradepath{Obligation closure requires checked carrier admission, unit-extension handoff, triangle-ledger exactness, readback nonescape, seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopRealCompletionAdjointUp.}
\end{closurestatus}
