\begin{theorem}[SpinGroup double-cover fiber ledger]
\label{thm:spingroup-double-cover-fiber-ledger}
The double-cover fiber ledger row exposed by $\SpinGroupUp$ is exactly the
Clifford-unit comparison, the parity $\mathsf{UnaryHistory}$ row, the
orthogonal-action endpoint, the $\Cont$ projection witness, and the
$\mathsf{Pkg}$ provenance. These five rows are the fiber face of
\autoref{def:spingroup-bhist-carrier-packet} and
\autoref{thm:spingroup-double-cover-fiber-classifier}; no host sign quotient
or ambient orthogonal-group equality is part of the ledger.
\end{theorem}
\leanchecked{BEDC.Derived.SpinGroupUp.SpinGroupRootCarrier\_double\_cover\_fiber\_ledger}
\begin{proof}
Project the carried packet through
\autoref{def:spingroup-bhist-carrier-packet}. The visible coordinates include
the Clifford unit data, parity history, action endpoint, continuation witness,
and package provenance.

Apply \autoref{thm:spingroup-double-cover-fiber-classifier}. It compares the
two carried spin endpoints only by the Clifford-unit comparison and the shared
orthogonal-action endpoint recorded in the package ledger.

The parity row and the $\Cont$ witness are the transport data that make this
comparison a fiber row. Since the classifier theorem exposes no other
constructor, the five displayed rows exhaust the ledger.
\end{proof}

\begin{theorem}[SpinGroup conjugation action readback]
\label{thm:spingroup-conjugation-action-readback}
The action row in \autoref{def:spingroup-bhist-carrier-packet} reads
conjugation only from the displayed Clifford product rows, Clifford inverse
rows, and $\hsame$ transport. It does not read a host action, a matrix action,
or an unrecorded orthogonal representation outside the $\SpinGroupUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.SpinGroupUp.SpinGroupRootCarrier\_conjugation\_action\_readback}
\begin{proof}
Unpack the action coordinate of
\autoref{def:spingroup-bhist-carrier-packet}. Its source rows are the
Clifford-unit endpoint, the multiplication ledger, the inverse ledger, and the
displayed $\hsame$ transports between the selected endpoints.

Use \autoref{thm:spingroup-group-consumer-boundary} to restrict downstream
reads to Clifford unit, multiplication, inverse, double-cover classifier, and
provenance rows. The conjugation action is therefore reconstructed from the
product-inverse-product spine already present in the packet.

The $\hsame$ rows transport the readback between classifier-equal endpoints.
No host action row is available after this projection, so the action readback
is exactly the displayed Clifford product and inverse readback.
\end{proof}

\begin{theorem}[SpinGroup boundary consumer exactness]
\label{thm:spingroup-boundary-consumer-exactness}
Every $\PinGroupUp$, $\LieGroupUp$, or $\CliffordUp$ consumer of the
$\SpinGroupUp$ boundary reads precisely the exported Clifford-unit source,
parity classifier, multiplication and inverse rows, conjugation readback,
double-cover fiber ledger, finite $\Cont$ witnesses, and $\mathsf{Pkg}$
provenance. No host orthogonal group, host quotient, or additional Clifford
carrier row is exported.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:spingroup-root-double-cover-consumer-exhaustion}. It
already confines root double-cover consumers to the visible Clifford unit,
parity, inverse, product, fiber classifier, continuation, and provenance rows.

Apply \autoref{thm:spingroup-double-cover-fiber-ledger} to replace the fiber
classifier by its exact ledger rows. Apply
\autoref{thm:spingroup-conjugation-action-readback} for the action coordinate;
that readback contributes only Clifford product, inverse, and $\hsame$
transport rows.

Finally use \autoref{thm:spingroup-group-consumer-boundary}. Its consumer
projection admits the same rows for $\PinGroupUp$, $\LieGroupUp$, and
$\CliffordUp$ consumers and admits no host orthogonal group or quotient row.
Thus the exported boundary is exact.
\end{proof}
\leanchecked{BEDC.Derived.SpinGroupUp.SpinGroupRootCarrier\_boundary\_consumer\_exactness}

\begin{theorem}[SpinGroup conjugation action product law]
\label{thm:spingroup-conjugation-action-product-law}
Let $S$ and $T$ be accepted $\SpinGroupUp$ packets of
\autoref{def:spingroup-bhist-carrier-packet}. Let $s$ and $t$ be their visible
Clifford-unit endpoints, let $s\cdot t$ be the endpoint supplied by the
packet's finite Clifford product row, and let $v$ be a Clifford-vector row
accepted by the same $\NameCert_{\CliffordUp}$ source. Write
$$
\mathsf{Act}_{s}(v):=(s\cdot v)\cdot s^{-1}
$$
for the conjugation endpoint read by the action row, and write $\sim_{\CliffordUp}$
for the generated $\CliffordUp$ classifier. Then the product action endpoint
and the iterated action endpoint are both accepted Clifford-vector action rows
in the $\SpinGroupUp$ packet, and
$$
\mathsf{Act}_{s\cdot t}(v)\sim_{\CliffordUp}
\mathsf{Act}_{s}(\mathsf{Act}_{t}(v)).
$$
The comparison keeps the same orthogonal-action endpoint and the same $\Pkg$
provenance ledger. It is a Clifford-row classifier comparison, not equality of
host linear maps, matrices, or an unrecorded orthogonal-group action.
\end{theorem}
\begin{proof}
Project the two accepted packets through
\autoref{def:spingroup-bhist-carrier-packet}. The visible data include the
Clifford-unit endpoints $s$ and $t$, the Clifford product row for $s\cdot t$,
the inverse rows for $s$, $t$, and $s\cdot t$, the action row on Clifford-vector
histories, the orthogonal-action endpoint, and the $\Pkg$ provenance rows.
By \autoref{thm:spingroup-clifford-group-consumer-boundary} and
\autoref{thm:spingroup-group-consumer-boundary}, no other action source is
available to the consumer.

Apply \autoref{thm:spingroup-conjugation-action-readback}. The action endpoint
for the product packet is read as the Clifford word
$$
((s\cdot t)\cdot v)\cdot (s\cdot t)^{-1}.
$$
The iterated action endpoint is read as the Clifford word
$$
(s\cdot ((t\cdot v)\cdot t^{-1}))\cdot s^{-1}.
$$
Both words are accepted Clifford rows because the action readback uses only
Clifford product rows, Clifford inverse rows, and $\hsame$ transport already
present in the packet.

The word comparison is the same BEDC group calculation as
\autoref{thm:group-conjugation-composition}, now read inside the Clifford-unit
surface. First, the inverse row for the product is the reversed inverse product
row supplied by \autoref{thm:group-inverse-mul-reverse}:
$$
(s\cdot t)^{-1}\sim_{\CliffordUp}t^{-1}\cdot s^{-1}.
$$
Multiplication congruence and associativity for the displayed product spine
transport this comparison through the outer Clifford products, so
$$
((s\cdot t)\cdot v)\cdot (s\cdot t)^{-1}
\sim_{\CliffordUp}
((s\cdot t)\cdot v)\cdot (t^{-1}\cdot s^{-1}).
$$
Reassociating the same finite product spine gives
$$
((s\cdot t)\cdot v)\cdot (t^{-1}\cdot s^{-1})
\sim_{\CliffordUp}
(s\cdot ((t\cdot v)\cdot t^{-1}))\cdot s^{-1}.
$$
The transport of each reassociation through the Clifford classifier is exactly
the product-stability row of \autoref{thm:clifford-product-stability-obligation}
inside the generated classifier of \autoref{def:clifford-classifier-package}.
Transitivity of that classifier gives the displayed comparison between
$\mathsf{Act}_{s\cdot t}(v)$ and $\mathsf{Act}_{s}(\mathsf{Act}_{t}(v))$.

It remains to identify the endpoint and provenance read by the public spin
boundary. The double-cover row is not recomputed from a host orthogonal group:
\autoref{thm:spingroup-double-cover-fiber-classifier} compares spin packets by
the Clifford-unit comparison together with the shared orthogonal-action
endpoint in the package ledger. The calculation above changes only the
parenthesization of the displayed Clifford product-inverse-product spine and
uses the product inverse row already named by the packet. Therefore the
orthogonal-action endpoint and the $\Pkg$ provenance row remain the same, and
the action product law is internal to the displayed $\SpinGroupUp$ boundary.
\end{proof}

\begin{theorem}[SpinGroup conjugation action identity law]
\label{thm:spingroup-conjugation-action-identity-law}
Let $S$ be an accepted $\SpinGroupUp$ packet of
\autoref{def:spingroup-bhist-carrier-packet} whose visible Clifford-unit
endpoint is the identity endpoint $e$. Let $v$ be any Clifford-vector row
accepted by the same $\NameCert_{\CliffordUp}$ source. Write
$$
\mathsf{Act}_{e}(v):=(e\cdot v)\cdot e^{-1}
$$
for the conjugation endpoint read by the action row, and write
$\sim_{\CliffordUp}$ for the generated $\CliffordUp$ classifier. Then
$\mathsf{Act}_{e}(v)$ is an accepted Clifford-vector action row in the same
$\SpinGroupUp$ packet and
$$
\mathsf{Act}_{e}(v)\sim_{\CliffordUp}v.
$$
The comparison uses only the displayed Clifford identity, inverse, product,
$\hsame$, $\Cont$, and $\Pkg$ rows; it does not use a host linear action, a
matrix model, or an ambient orthogonal-group equality.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:spingroup-bhist-carrier-packet}. The visible
coordinates include the Clifford identity endpoint $e$, the inverse row for
$e$, the finite product rows with Clifford-vector rows, the action row, the
classifier row generated by the Clifford classifier and $\hsame$ transport,
and the $\Pkg$ provenance for these rows. By
\autoref{thm:spingroup-clifford-group-consumer-boundary} and
\autoref{thm:spingroup-group-consumer-boundary}, no other action source is
available to the consumer.

Apply \autoref{thm:spingroup-conjugation-action-readback}. The action endpoint
for the identity packet is read as the Clifford word
$$
(e\cdot v)\cdot e^{-1}.
$$
This word is an accepted Clifford action row because the readback uses only the
packet's Clifford product rows, inverse rows, and endpoint transports.

The identity endpoint is carried as the same unit row on the Clifford and
$\GroupUp$ sides of the packet. The inverse row for the identity endpoint is
therefore classified with the identity endpoint by the group inverse law over
that carried Clifford-unit surface. Transporting this inverse comparison
through the right product context gives
$$
(e\cdot v)\cdot e^{-1}\sim_{\CliffordUp}(e\cdot v)\cdot e.
$$
The transport is an instance of the product-stability row of
\autoref{thm:clifford-product-stability-obligation} inside the generated
classifier of \autoref{def:clifford-classifier-package}.

Now apply the two displayed identity laws in the same finite product spine.
The right identity law collapses the final factor:
$$
(e\cdot v)\cdot e\sim_{\CliffordUp}e\cdot v.
$$
The left identity law collapses the initial factor:
$$
e\cdot v\sim_{\CliffordUp}v.
$$
Transitivity of the generated $\CliffordUp$ classifier composes these three
rows and gives
$$
(e\cdot v)\cdot e^{-1}\sim_{\CliffordUp}v.
$$
Substituting the action readback notation yields
$\mathsf{Act}_{e}(v)\sim_{\CliffordUp}v$.

The calculation has changed only the displayed Clifford product-inverse-product
word by inverse and unit rows already present in the packet. The orthogonal
readback and $\Pkg$ provenance are not recomputed from any host representation,
so the identity action law is internal to the public $\SpinGroupUp$ boundary.
\end{proof}

\begin{theorem}[SpinGroup conjugation action inverse-involution law]
\label{thm:spingroup-conjugation-action-inverse-involution-law}
Let $S$ be an accepted $\SpinGroupUp$ packet of
\autoref{def:spingroup-bhist-carrier-packet} with visible Clifford-unit
endpoint $s$, inverse endpoint $s^{-1}$, identity endpoint $e$, and displayed
left-inverse row
$$
s^{-1}\cdot s\sim_{\CliffordUp}e.
$$
Let $v$ be a Clifford-vector row accepted by the same
$\NameCert_{\CliffordUp}$ source. Write
$$
\mathsf{Act}_{s}(v):=(s\cdot v)\cdot s^{-1}
$$
for the conjugation endpoint read by the action row, and write
$\sim_{\CliffordUp}$ for the generated $\CliffordUp$ classifier. Then the
iterated endpoint
$$
\mathsf{Act}_{s^{-1}}(\mathsf{Act}_{s}(v))
$$
is an accepted Clifford-vector action row in the same $\SpinGroupUp$ packet and
$$
\mathsf{Act}_{s^{-1}}(\mathsf{Act}_{s}(v))\sim_{\CliffordUp}v.
$$
The comparison is the displayed inverse-cancellation row of the Clifford-unit
ledger transported through the conjugation readback; it is not equality of host
linear maps, matrices, or an ambient orthogonal-group action.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:spingroup-bhist-carrier-packet}. The packet
contains the Clifford-unit endpoint $s$, its inverse endpoint $s^{-1}$, the
identity endpoint $e$, product rows for $s^{-1}\cdot s$, the action row on
Clifford-vector histories, the generated $\CliffordUp$ classifier, and the
$\Pkg$ provenance for these rows. By
\autoref{thm:spingroup-clifford-group-consumer-boundary} and
\autoref{thm:spingroup-group-consumer-boundary}, this is the whole readable
surface for the downstream action calculation.

Apply \autoref{thm:spingroup-conjugation-action-product-law} with outer spin
endpoint $s^{-1}$ and inner spin endpoint $s$. The product endpoint and the
iterated action endpoint are accepted Clifford-vector action rows in the same
packet, and the product law gives
$$
\mathsf{Act}_{s^{-1}\cdot s}(v)
\sim_{\CliffordUp}
\mathsf{Act}_{s^{-1}}(\mathsf{Act}_{s}(v)).
$$
By symmetry of the generated classifier, it is enough to compare
$\mathsf{Act}_{s^{-1}\cdot s}(v)$ with $v$.

The displayed left-inverse row in the carried $\GroupUp$ surface identifies the
Clifford-unit product endpoint with the identity endpoint:
$$
s^{-1}\cdot s\sim_{\CliffordUp}e.
$$
This row is read on the Clifford side through the same multiplication and
inverse coordinates used by the action readback. Applying
\autoref{thm:spingroup-conjugation-action-readback}, the two action endpoints
are the Clifford words
$$
((s^{-1}\cdot s)\cdot v)\cdot (s^{-1}\cdot s)^{-1}
$$
and
$$
(e\cdot v)\cdot e^{-1}.
$$
Transport the comparison $s^{-1}\cdot s\sim_{\CliffordUp}e$ through the left
factor of the first word by \autoref{thm:clifford-product-stability-obligation}.
For the inverse factor, apply inverse congruence from the carried $\GroupUp$
rows, equivalently the inverse-congruence field listed in
\autoref{def:group-stability-certificate}, and then transport the resulting
comparison through the right product context using the same Clifford product
stability. Thus
$$
\mathsf{Act}_{s^{-1}\cdot s}(v)
\sim_{\CliffordUp}
\mathsf{Act}_{e}(v).
$$

Now apply \autoref{thm:spingroup-conjugation-action-identity-law} to the
identity endpoint in the same packet:
$$
\mathsf{Act}_{e}(v)\sim_{\CliffordUp}v.
$$
Transitivity of the generated classifier composes the product-law comparison,
the transported inverse-cancellation comparison, and the identity-action
comparison, giving
$$
\mathsf{Act}_{s^{-1}}(\mathsf{Act}_{s}(v))\sim_{\CliffordUp}v.
$$
The accepted-row assertion for the iterated endpoint was already supplied by
the product-law application, and every transport used above is a displayed
Clifford product, inverse, $\hsame$, $\Cont$, or $\Pkg$ row of the same
$\SpinGroupUp$ packet.
\end{proof}

\begin{theorem}[SpinGroup conjugation action classifier congruence]
\label{thm:spingroup-conjugation-action-classifier-congruence}
Let $S$ be an accepted $\SpinGroupUp$ packet of
\autoref{def:spingroup-bhist-carrier-packet}. Let $s$ and $s'$ be visible
Clifford-unit endpoints of $S$ with
$s\sim_{\CliffordUp}s'$. Let $v$ and $v'$ be Clifford-vector rows accepted by
the same $\NameCert_{\CliffordUp}$ source with
$v\sim_{\CliffordUp}v'$. Write
$$
\mathsf{Act}_{s}(v):=(s\cdot v)\cdot s^{-1}
$$
for the conjugation endpoint read by the action row, and write
$\sim_{\CliffordUp}$ for the generated $\CliffordUp$ classifier. Then
$\mathsf{Act}_{s}(v)$ and $\mathsf{Act}_{s'}(v')$ are accepted
Clifford-vector action rows in the same $\SpinGroupUp$ packet, and
$$
\mathsf{Act}_{s}(v)\sim_{\CliffordUp}\mathsf{Act}_{s'}(v').
$$
The comparison is the classifier transport of the displayed
product-inverse-product word; it does not use equality of host linear maps,
matrices, or an unrecorded orthogonal action.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:spingroup-bhist-carrier-packet}. The visible
rows include the Clifford-unit endpoints $s$ and $s'$, the Clifford-vector
rows $v$ and $v'$, the finite Clifford product rows, the inverse rows supplied
through the carried $\GroupUp$ surface, the action row on vector histories,
the generated $\CliffordUp$ classifier, and the $\Pkg$ provenance tying these
rows to the same packet. By
\autoref{thm:spingroup-clifford-group-consumer-boundary} and
\autoref{thm:spingroup-group-consumer-boundary}, no other action source is
available to a consumer of this packet.

Apply \autoref{thm:spingroup-conjugation-action-readback}. The two action
endpoints are read as the Clifford words
$$
(s\cdot v)\cdot s^{-1}
$$
and
$$
(s'\cdot v')\cdot (s')^{-1}.
$$
These are accepted action rows because the readback uses only Clifford product
rows, Clifford inverse rows, and $\hsame$ transport already present in $S$.

The displayed comparison $s\sim_{\CliffordUp}s'$ lies in the Clifford-unit
surface carried by the same packet. The inverse-congruence row listed in
\autoref{def:group-stability-certificate}, read through that carried group
surface, transports it to
$$
s^{-1}\sim_{\CliffordUp}(s')^{-1}.
$$
Now apply the product-stability row of
\autoref{thm:clifford-product-stability-obligation} inside the generated
classifier of \autoref{def:clifford-classifier-package}. Applied first to
$s\sim_{\CliffordUp}s'$ and $v\sim_{\CliffordUp}v'$, it gives
$$
s\cdot v\sim_{\CliffordUp}s'\cdot v'.
$$
Applied again to this product comparison and to the inverse comparison above,
it gives
$$
(s\cdot v)\cdot s^{-1}
\sim_{\CliffordUp}
(s'\cdot v')\cdot (s')^{-1}.
$$
Substituting the action readback notation yields the asserted classifier row
between $\mathsf{Act}_{s}(v)$ and $\mathsf{Act}_{s'}(v')$.

All rows used in the calculation are read from the same $\NameCert_{\CliffordUp}$
source and the same accepted $\SpinGroupUp$ packet: the two input classifier
comparisons, the inverse-congruence row, the two Clifford product-stability
transports, the action readback, and the provenance ledger. Hence the
congruence is internal to the packet and keeps the action endpoint within the
same public $\SpinGroupUp$ boundary.
\end{proof}
