\begin{theorem}[SpinGroup root double-cover consumer exhaustion]
\label{thm:spingroup-root-double-cover-consumer-exhaustion}
A downstream $\PinGroupUp$ or $\CliffordUp$ consumer of the $\SpinGroupUp$ root
double-cover boundary can read only the visible Clifford unit source, the
parity classifier, inverse and product witnesses, the double-cover fiber
classifier, finite $\Cont$ readbacks, and $\mathsf{Pkg}$ provenance. These are
exactly the rows exposed by
\autoref{def:spingroup-bhist-carrier-packet},
\autoref{def:spingroup-root-bhist-carrier},
\autoref{thm:spingroup-root-namecert-threshold-package},
\autoref{thm:spingroup-double-cover-fiber-classifier}, and
\autoref{thm:spingroup-namecert-obligation-surface}.
\end{theorem}
\begin{proof}
Project a consumer read through
\autoref{thm:spingroup-namecert-obligation-surface}. The obligation surface
lists the carrier, classifier, stability, exactness, and ledger rows available
to any downstream consumer.

Apply \autoref{thm:spingroup-root-namecert-threshold-package} to the root part.
It confines carrier reads to the visible Clifford unit source, parity ledger,
inverse and product witnesses, finite $\Cont$ transport, $\hsame$ comparison,
and $\mathsf{Pkg}$ provenance. The concrete packet definitions provide no
other constructor to inspect.

Finally apply \autoref{thm:spingroup-double-cover-fiber-classifier} to the
projection boundary. The only extra classifier available there is the
double-cover fiber classifier, and it is again a displayed finite
$\mathsf{BHist}$ row. Repacking the projected rows gives exactly the consumer
surface named in the statement, with no host quotient, ambient orthogonal group
equality, analytic covering datum, or standard-bridge datum.
\end{proof}
\leanchecked{BEDC.Derived.SpinGroupUp.SpinGroupRootCarrier\_double\_cover\_consumer\_exhaustion}

\begin{corollary}[SpinGroup BHist packet strict obstruction]
\label{cor:spingroup-bhist-packet-strict-obstruction}
Let a displayed $\SpinGroupUp$ $\BHist$ packet row be used as a failure, refusal, separation, or countermodel row against a converse double-cover read or against reuse by a downstream consumer. Then the obstruction is strict and local: it blocks only the named route whose readback asks for one of the exported packet coordinates, namely the Clifford-even lift row, the even $\UnaryHistory$ parity ledger, the double-cover projection endpoint, the projection $\Cont$ witness, the $\hsame$ classifier row, or the cited $\NameCert_{\CliffordUp}$ and $\NameCert_{\GroupUp}$ source rows. It cannot be reinterpreted as a global impossibility for spin groups, as a host theorem about Clifford or orthogonal groups, or as hidden external validation of an unlisted route.
\end{corollary}
\begin{proof}
Start with the displayed obstruction row and read it through the public double-cover boundary of \autoref{thm:spingroup-spin-double-cover-boundary}. That boundary has only one consumer-facing readback: the projection endpoint together with its $\Cont$ witness from the Clifford-even lift. Exactness in the same theorem forces any public spin-boundary use to recover the Clifford-even lift row, the even $\UnaryHistory$ parity ledger, and the projection continuation from the same finite $\BHist$ packet. A row that is not one of these readback coordinates is therefore not a boundary coordinate for the converse route.

Now apply the source-scope theorem \autoref{thm:spingroup-root-carrier-source-scope}. Every root carrier row is sourced through $\NameCert_{\CliffordUp}$ or $\NameCert_{\GroupUp}$: the Clifford endpoint, unit-like endpoint, product transport, and inverse transport rows are read from the Clifford certificate, while the singleton-history group-law rows are read from the group certificate over the same unary history. No third source row is admitted by the $\SpinGroupUp$ root carrier.

Consequently any consumer-facing use of the obstruction must factor through the displayed list: source rows from $\NameCert_{\CliffordUp}$ and $\NameCert_{\GroupUp}$, the Clifford-even lift, the parity ledger, the projection endpoint, the projection $\Cont$ witness, and the $\hsame$ classifier movement. If the proposed converse or reuse route asks for one of those rows and the displayed failure, refusal, separation, or countermodel row denies that coordinate, the route is blocked.

The same factorization also rejects stronger readings. A global impossibility statement would require a row ranging over spin groups outside this finite packet; a host theorem would require a Clifford, orthogonal, quotient, matrix, or topological source not supplied by the two certificates; and hidden external validation would require an accepted route not listed among the boundary readback and source-scope rows. The cited boundary and source-scope theorems provide none of those coordinates. The obstruction is therefore only a local negative certificate for the named converse or reuse route inside the displayed $\SpinGroupUp$ $\BHist$ packet.
\end{proof}
