\begin{theorem}[Real completeness selector route coverage]
\label{thm:real-completeness-selector-route-coverage}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet, and let
$$
L=(R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L)
$$
be an accepted $\LimitSelectorUp$ packet whose selected observation is the displayed diagonal observation consumed from $R$. Every selected diagonal observation consumed by a $\RealUp$ reader or a $\CauchyLimitSealUp$ reader factors through the finite $\LimitSelectorUp$ route
$$
n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L
$$
and through the $\RealCompletenessUp$ rows
$$
\mu,\Delta,D,W,Q,S,H,C,P,N.
$$
The coverage is a finite route statement: it names the reader path that reaches the common seal row $S$, and it does not export a host-selected limit, quotient-stream equality, countable-choice selector, host equality, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First expose the selector side. Apply \autoref{thm:limit-selector-namecert-obligations} to read the packet rows of $L$, and use \autoref{thm:limit-selector-finite-witness-route} to force every selected diagonal-limit read through $n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$.

Next compare the selected observation with the $\RealCompletenessUp$ diagonal rows. The handoff theorem \autoref{thm:real-completeness-limitselector-handoff} identifies the selector route with the diagonal read of $R$, while \autoref{thm:real-completeness-modulus-diagonal-exactness} pins that read to $\mu,\Delta,D,W,Q$.

Finally bind the consumer endpoint. Apply \autoref{thm:real-completeness-limit-uniqueness-classifier} to keep the transported seal-ledger classifier fixed, and apply \autoref{thm:real-completeness-nonescape-boundary} to rule out the listed external completion objects.
\end{proof}

\begin{theorem}[Real completeness modulus-selector factorization]
\label{thm:real-completeness-modulus-selector-factorization}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. The modulus row and the selector row are not independently readable by any selected-observation consumer. Every selected index is justified first by the displayed modulus row $\mu$, then by the selector row $\Delta$, and then by the finite route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the $\RealUp$ seal rows $D,W,Q,S$. The remaining transport, continuation, package, and local naming rows $H,C,P,N$ record the same route for downstream seal consumers.
\end{theorem}
\begin{proof}
Begin with the modulus obligation. The RealCompleteness obligations bind every precision request to the displayed modulus row, and \autoref{thm:real-completeness-modulus-diagonal-exactness} turns the selected diagonal read into a route through $\mu,\Delta,D,W,Q$.

The selector cannot be detached from that modulus route. When the observation is presented through $\LimitSelectorUp$, \autoref{thm:limit-selector-namecert-obligations} and \autoref{thm:limit-selector-finite-witness-route} expose only the finite selector rows, and \autoref{thm:real-completeness-limitselector-handoff} identifies those rows with the same $\mu,\Delta,D,W,Q$ diagonal read.

It remains to seal the endpoint. Apply \autoref{thm:real-completeness-limit-uniqueness-classifier} and \autoref{thm:real-completeness-nonescape-boundary}. The first fixes the seal-ledger classifier along $S,H,C,P,N$, and the second excludes an independent quotient, host, choice, or ambient-completeness interpretation of the selected index.
\end{proof}

\begin{theorem}[Real completeness seal consumer exhaustion]
\label{thm:real-completeness-seal-consumer-exhaustion}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet, and let
$$
L=(R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L)
$$
be an accepted $\LimitSelectorUp$ packet reading a selected diagonal observation from $R$. Every downstream consumer of the shared seal exhausts the same finite route: it consumes the selector rows $n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$ when the observation is selector-presented, consumes the RealCompleteness rows $\mu,\Delta,D,W,Q,S,H,C,P,N$ when the observation is read from $R$, and exports no quotient stream, selected host limit, countable-choice selector, host equality, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First route the selector-presented observation. Theorems~\ref{thm:limit-selector-namecert-obligations} and~\ref{thm:limit-selector-finite-witness-route} expose the selector rows and give the finite witness route to the common seal row $S$.

Now route the same observation from the $\RealCompletenessUp$ packet. Use \autoref{thm:real-completeness-modulus-diagonal-exactness} for the diagonal rows and \autoref{thm:real-completeness-limitselector-handoff} for the comparison between the selector packet and $R$.

Finally exhaust the downstream consumer surface. Apply \autoref{thm:real-completeness-limit-uniqueness-classifier} to keep the seal-ledger classifier determined by the displayed rows, and apply \autoref{thm:real-completeness-nonescape-boundary} to exclude quotient streams, host-selected limits, countable-choice selectors, host equality, and ambient completeness from the export surface.
\end{proof}

\begin{theorem}[RealCompleteness diagonal seal factorization public boundary]
\label{thm:real-completeness-diagonal-seal-factorization-public-boundary}
Every accepted $\RealCompletenessUp$ diagonal-limit packet consumed by a $\RealUp$- or $\CauchyLimitSealUp$-facing reader factors through the displayed $\DyadicRatCoreUp$ ledger, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\CauchyLimitSealUp$ boundary, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\RealCompletenessUp}$ row. The public read exports no quotient stream, no selected host limit, no host real equality, no choice datum, and no ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted $\RealCompletenessUp$ carrier. Its diagonal-limit rows expose the dyadic ledger, stream windows, regular-sequence readback, Cauchy-limit seal boundary, transports, routes, provenance, and local naming row as the only public coordinates.

Apply the diagonal witness schedule and finite witness rows already displayed in the chapter. They route every precision request through the modulus and diagonal selector before a $\RealUp$- or $\CauchyLimitSealUp$-facing reader can see the observation.

Now route the seal-facing read. The $\CauchyLimitSealUp$ boundary and $\RegSeqRatUp$ readback carry the observation back to the displayed finite ledger, while the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows record the same transport and provenance for the public consumer.

The non-escape conclusion is immediate from the carrier inventory. Since no quotient stream, selected host limit, host real equality, choice datum, or ambient completeness theorem is a coordinate of the packet, none can be exported by the public factorization route.
\end{proof}

\begin{theorem}[Real completeness finite approximation LimitSelector handoff]
\label{thm:real-completeness-finite-approximation-limit-selector-handoff}
Let
$$
F=(R_F,n_F,k_F,W_F,D_F,E_F,S_F,H_F,C_F,P_F,N_F)
$$
be an accepted $\FiniteCauchyApproximationUp$ packet, let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ diagonal-limit packet consuming the finite approximation row, and let
$$
L=(R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L)
$$
be a compatible accepted $\LimitSelectorUp$ packet reading the same selected diagonal observation. If the finite approximation route of $F$ supplies the source row, selected precision, threshold, finite window, dyadic observation ledger, explicit error row, and handoff row consumed by $R$, and if the selected observation of $L$ agrees through the displayed transports with the same diagonal rows of $R$, then every $\RealUp$-, $\CauchyLimitSealUp$-, selector-facing, and completion-facing consumer factors through the same displayed rows
$$
X,\mu,\Delta,D,W,Q,S,H,C,P,N
$$
and the selector rows
$$
n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L.
$$
The handoff contains the finite approximation route of $F$, the diagonal seal route of $R$, and the selected finite witness route of $L$ only. It exports no quotient stream, no selected host limit, no countable-choice selector, no host equality, no hidden completion coordinate, and no ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the finite approximation packet. Theorems~\ref{thm:finite-cauchy-approximation-real-handoff} and~\ref{thm:finite-cauchy-approximation-seal-coverage} force every consumer of $F$ to read the displayed source, precision, threshold, finite window, dyadic ledger, error row, handoff row, transports, continuation routes, provenance, and local naming rows before any $\RealUp$ or $\CauchyLimitSealUp$ boundary is visible.

Next attach the diagonal-limit packet. The finite approximation handoff is consumed by the $\RealCompletenessUp$ rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$, and the diagonal seal totality theorem routes the completion-facing read through the same seal row $S$ rather than through an independent limit object.

Now attach the selector packet. Apply \autoref{thm:real-completeness-limitselector-handoff} and \autoref{thm:real-completeness-selector-route-coverage}: the selected observation reaches $S$ only through $n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$, and these rows are identified with the same diagonal read of $R$ through the displayed transports.

Finally exhaust the consumer surface. Theorems~\ref{thm:real-completeness-scoped-consumer-seal-exhaustion} and~\ref{thm:real-completeness-diagonal-seal-factorization-public-boundary} leave no remaining route outside the finite approximation, diagonal, and selector rows already displayed. Hence quotient streams, selected host limits, countable-choice selectors, host equality, hidden completion coordinates, and ambient completeness are not exported by the handoff.
\end{proof}

\begin{theorem}[RealCompleteness diagonal example consumer lattice]
\label{thm:real-completeness-diagonal-example-consumer-lattice}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. Suppose a $\LimitSelectorUp$ packet reads a selected diagonal observation from $R$, and suppose, when available, a $\CauchySequenceSpaceUp$ presentation supplies the same observation through a shared finite Cauchy window. Then the accepted data generate a finite consumer lattice over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyLimitSealUp$, $\LimitSelectorUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows: every completion-facing, seal-facing, selector-facing, and shared-window read factors through the displayed diagonal schedule, witness windows, readback rows, seal row, classifier transports, continuation routes, package provenance, and local naming rows.

The lattice exports no $\RealUp$ completeness theorem, no quotient stream, no selected host limit, no countable-choice selector, no host equality, and no ambient completeness row.
\end{theorem}
\begin{proof}
First route the selected diagonal observation. Theorems~\ref{thm:real-completeness-limitselector-handoff} and~\ref{thm:real-completeness-diagonal-seal-totality} bind the $\LimitSelectorUp$ read and the $\RealCompletenessUp$ diagonal seal to the same finite rows $X,\mu,\Delta,D,W,Q,S,H,C,P,N$.

When the observation is also presented through a shared finite Cauchy window, apply \autoref{thm:real-completeness-cauchysequence-space-shared-window-handoff}. This places the $\CauchySequenceSpaceUp$ presentation on the same window and seal route rather than adding an independent completion surface.

Now exhaust the downstream consumer routes. Theorem~\ref{thm:real-completeness-seal-consumer-exhaustion} says that selector-facing and RealCompleteness-facing consumers use exactly the displayed finite rows, while \autoref{thm:real-completeness-diagonal-seal-factorization-public-boundary} identifies the public boundary seen by $\RealUp$-, $\CauchyLimitSealUp$-, and completion-facing readers.

The stated non-export claims follow from that factorization. None of a $\RealUp$ completeness theorem, quotient stream, selected host limit, countable-choice selector, host equality, or ambient completeness row is a coordinate of the factorized lattice, so none is exported by the consumer package.
\end{proof}

\begin{theorem}[Real completeness shared-tail modulus handoff]
\label{thm:real-completeness-shared-tail-modulus-handoff}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ carrier. Suppose a completion-facing consumer presents the selected diagonal observation through an accepted $\CauchySharedTailModulusUp$ packet. Then the consumer route factors first through the shared threshold row $\tau$, then through the dyadic ledger, both $\StreamNameUp$ windows, both $\RegSeqRatUp$ readbacks, and finally through the same $\RealUp$ seal row $S$ displayed by $R$.

The route contains no pair of independent thresholds, no quotient stream equality, no host real equality, no selected host limit, no countable-choice selector, and no ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the diagonal-limit side. Theorems~\ref{thm:real-completeness-diagonal-seal-factorization-public-boundary} and~\ref{thm:real-completeness-diagonal-example-consumer-lattice} force every completion-facing read of $R$ through $X,\mu,\Delta,D,W,Q,S,H,C,P,N$ before the $\RealUp$ seal row can be consumed.

Now attach the shared-tail packet. Apply \autoref{thm:cauchy-shared-tail-modulus-tail-synchronization}: both regular-Cauchy presentations are synchronized by the single threshold row $\tau$ before either window is read. Apply \autoref{thm:cauchy-shared-tail-modulus-real-seal-handoff}: the synchronized tails then pass through the dyadic ledger, the two $\StreamNameUp$ windows, and the two $\RegSeqRatUp$ readbacks before reaching the real-facing seal row.

It remains to compare endpoints. The RealCompleteness factorization identifies that seal-facing endpoint with the displayed row $S$ of $R$. Finally, \autoref{thm:real-completeness-nonescape-boundary} excludes independent thresholds, quotient stream equality, host real equality, selected limits, countable choice, and ambient completeness from the exported route.
\end{proof}

\begin{theorem}[Real completeness selector-window-seal factorization]
\label{thm:real-completeness-selector-window-seal-factorization}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. Every selected diagonal observation consumed from $R$ factors in the strict order
$$
\mu,\Delta,D,W,Q,S.
$$
The modulus row $\mu$ supplies the finite request, the selector row $\Delta$ selects the displayed diagonal observation, the $\DyadicRatCoreUp$ ledger $D$ records the dyadic value, the $\StreamNameUp$ windows $W$ expose the finite observation windows, the $\RegSeqRatUp$ readback $Q$ returns the regular-sequence row, and the $\RealUp$ seal $S$ is reachable only after those rows have been displayed. The rows $H,C,P,N$ carry transport, route replay, provenance, and local naming for this same factorization and carry no independent selector, window, limit, quotient, choice, host-equality, or ambient-completeness object.
\end{theorem}
\begin{proof}
Start with selector route coverage. Theorem~\ref{thm:real-completeness-selector-route-coverage} says that every selected diagonal observation reaches a $\RealUp$ or $\CauchyLimitSealUp$ reader only through the displayed selector route and the $\RealCompletenessUp$ rows $\mu,\Delta,D,W,Q,S,H,C,P,N$.

Next factor the front of the route. The modulus-selector factorization theorem forces the selected index to pass first through $\mu$, then through $\Delta$, and then through the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows $D,W,Q,S$.

Now seal the consumer boundary. The seal consumer exhaustion theorem leaves no downstream route outside the selector-presented rows and the displayed $\RealCompletenessUp$ rows, while the nonescape boundary excludes quotient streams, host-selected limits, countable-choice selectors, host equality, and ambient completeness.

Thus $H,C,P,N$ can only transport, replay, authenticate, and name the same ordered route. They do not supply another selected observation or another seal endpoint.
\end{proof}

\begin{theorem}[Real completeness selector-window source determinacy]
\label{thm:real-completeness-selector-window-source-determinacy}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. Every accepted selector-window-seal read of $R$ reads the modulus row $\mu$ before it reads the selector row $\Delta$, and it reads $\Delta$ before any of the dyadic, stream-window, regular-sequence, or real-seal rows $D,W,Q,S$. The transport, route, package, and local naming rows $H,C,P,N$ can replay and certify that order, but they cannot supply an alternate source for the selected observation.
\end{theorem}
\begin{proof}
Start with selector route coverage. Theorem~\ref{thm:real-completeness-selector-route-coverage} makes every selected diagonal observation pass through the displayed selector route before it can be read by a $\RealUp$ or $\CauchyLimitSealUp$ consumer.

Now apply the modulus-selector factorization. Theorem~\ref{thm:real-completeness-modulus-selector-factorization} fixes the front of that route: the finite request is supplied by $\mu$, the selected diagonal row is supplied by $\Delta$, and the middle certificate rows $D,W,Q,S$ are reached only after that source pair is displayed.

Finally compare with the selector-window-seal factorization. Theorem~\ref{thm:real-completeness-selector-window-seal-factorization} identifies $H,C,P,N$ as transport, replay, provenance, and naming rows for the same ordered packet. Hence no accepted read can swap the source order or introduce a second source row.
\end{proof}

\begin{theorem}[Real completeness selector-window dyadic-window nonescape]
\label{thm:real-completeness-selector-window-dyadic-window-nonescape}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. In every selector-window-seal read of $R$, the middle rows $D,W,Q$ expose only the displayed $\DyadicRatCoreUp$ ledger, $\StreamNameUp$ windows, and $\RegSeqRatUp$ readback attached to the source rows $\mu,\Delta$. They cannot export quotient streams, host equality, choice selectors, selected host limits, or ambient completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:real-completeness-selector-window-source-determinacy} first. It places $D,W,Q$ downstream of the displayed source rows $\mu,\Delta$, so the middle rows are read as certificate rows for that selected observation rather than as independent completion data.

Next apply the nonescape boundary. Theorem~\ref{thm:real-completeness-nonescape-boundary} excludes quotient streams, host-selected limits, countable-choice selectors, host equality, and ambient completeness from the public $\RealCompletenessUp$ export.

The selector-window-seal factorization then pins the same exclusion to the middle rows. Since $D,W,Q$ are the dyadic ledger, finite stream-window display, and regular-sequence readback inside the ordered route, they have no coordinate from which any of the excluded objects could be exported.
\end{proof}

\begin{theorem}[Real completeness selector-window consumer readback]
\label{thm:real-completeness-selector-window-consumer-readback}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. Every $\RealUp$, $\CauchyLimitSealUp$, selector-facing, and completion-facing consumer of the selector-window-seal surface reads back the same displayed route
$$
\mu,\Delta,D,W,Q,S,H,C,P,N.
$$
No such consumer obtains a second modulus row, selector row, dyadic ledger, stream window, regular-sequence readback, seal row, transport, route replay, package provenance, or local naming row.
\end{theorem}
\begin{proof}
First exhaust the seal-facing consumers. Theorem~\ref{thm:real-completeness-seal-consumer-exhaustion} says that $\RealUp$, $\CauchyLimitSealUp$, selector-facing, and completion-facing reads use the selector-presented rows and the displayed $\RealCompletenessUp$ rows.

Next attach the shared-tail handoff. Theorem~\ref{thm:real-completeness-shared-tail-modulus-handoff} identifies the completion-facing route through the shared threshold, dyadic ledger, stream windows, regular-sequence readbacks, and the same real-facing seal row $S$.

Finally apply terminal export. Theorem~\ref{thm:real-completeness-selector-window-terminal-export} exports exactly the selector-window-seal packet, and \autoref{thm:real-completeness-selector-window-dyadic-window-nonescape} removes the possible middle-row escape routes. Thus every listed consumer reads back the same displayed $\mu,\Delta,D,W,Q,S,H,C,P,N$ route.
\end{proof}

\begin{theorem}[Real completeness selector-window terminal export]
\label{thm:real-completeness-selector-window-terminal-export}
Let $R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)$ be an accepted $\RealCompletenessUp$ packet. Once the ordered route
$$
\mu,\Delta,D,W,Q,S,H,C,P,N
$$
is displayed, every terminal completion-facing export of $R$ factors through the same selector-window-seal packet. The export cannot introduce quotient streams, host-selected limits, countable choice, host equality, hidden completion coordinates, or ambient completeness beyond the rows already displayed by the selector-window-seal factorization.
\end{theorem}
\begin{proof}
Start with selector route coverage. Theorem~\ref{thm:real-completeness-selector-route-coverage} routes selected observations through the displayed $\RealCompletenessUp$ rows before a $\RealUp$ or $\CauchyLimitSealUp$ reader can consume the seal endpoint.

Next use the modulus-selector factorization. Theorem~\ref{thm:real-completeness-modulus-selector-factorization} forces the front of the terminal route through $\mu$ and $\Delta$, then through the dyadic, stream-window, regular-sequence, and real-seal rows $D,W,Q,S$.

Now exhaust the seal-facing consumer. Theorem~\ref{thm:real-completeness-seal-consumer-exhaustion} leaves no downstream route outside the selector-presented rows, and \autoref{thm:real-completeness-selector-window-seal-factorization} identifies the ordered packet used by the terminal reader.

Finally apply \autoref{thm:real-completeness-nonescape-boundary}. It excludes quotient streams, host-selected limits, countable-choice selectors, host equality, hidden completion coordinates, and ambient completeness, so the terminal export is exactly the displayed selector-window-seal packet.
\end{proof}

\begin{theorem}[Real completeness tail-fiber selector compatibility]
\label{thm:real-completeness-tail-fiber-selector-compatibility}
Let
$$
R=(X,\mu,\Delta,D,W,Q,S,H,C,P,N)
$$
be an accepted $\RealCompletenessUp$ packet. Let
$$
L=(R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L)
$$
be a compatible accepted $\LimitSelectorUp$ packet reading the selected diagonal observation of $R$. Let
$$
F=(R_0,R_1,W_0,W_1,D_0,D_1,T,A,H_F,C_F,P_F,N_F)
$$
be an accepted $\RegularCauchyTailFiberUp$ packet whose paired windows and dyadic ledgers present that same selected observation to $\RealTailAgreementSealUp$. Then every completion-facing consumer of this combined presentation factors through one finite route: on the $\RealCompletenessUp$ side it reads
$$
\mu,\Delta,D,W,Q,S,H,C,P,N,
$$
on the $\LimitSelectorUp$ side it reads
$$
R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L,
$$
and on the tail-fiber side it reads
$$
R_0,R_1,W_0,W_1,D_0,D_1,T,A,H_F,C_F,P_F,N_F.
$$
The compatibility exports no quotient stream, host real equality, countable-choice selector, selected host limit, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First route the selected diagonal observation through the $\LimitSelectorUp$ packet. Apply \autoref{thm:limit-selector-namecert-obligations} and \autoref{thm:limit-selector-finite-witness-route} to expose $R_L,n,\mu_L,k_L,W_L,D_L,S,H_L,C_L,P_L,N_L$, then use \autoref{thm:real-completeness-limitselector-handoff} to identify that selector read with the displayed diagonal rows of $R$.

Next route the same observation from the $\RealCompletenessUp$ side. Apply \autoref{thm:real-completeness-selector-route-coverage}, \autoref{thm:real-completeness-modulus-selector-factorization}, and \autoref{thm:real-completeness-selector-window-seal-factorization} to force the read through $\mu,\Delta,D,W,Q,S,H,C,P,N$.

Use the terminal export theorem. By \autoref{thm:real-completeness-selector-window-terminal-export}, a completion-facing consumer cannot leave the displayed selector-window-seal packet after that route has been exposed.

Now compare the shared-tail presentation. Theorem~\ref{thm:regular-cauchy-tail-fiber-shared-seal-factorization} makes the $\RegularCauchyTailMeetUp$ route and the $\RealTailAgreementSealUp$ route share the row $T$ before the seal row $A$ is read, while \autoref{thm:regular-cauchy-tail-fiber-paired-window-exactness} fixes their common support to $R_0,R_1,W_0,W_1,D_0,D_1,T$.

Finally exhaust all consumer surfaces. Apply \autoref{thm:regular-cauchy-tail-fiber-seal-consumer-exhaustion} to keep every tail-fiber consumer inside $R_0,R_1,W_0,W_1,D_0,D_1,T,A,H_F,C_F,P_F,N_F$, then apply \autoref{thm:real-completeness-nonescape-boundary} and \autoref{thm:regular-cauchy-tail-fiber-nonescape}. The two non-escape boundaries exclude quotient streams, host real equality, countable-choice selectors, selected host limits, and ambient completeness, so the combined presentation has exactly three displayed finite routes: $\RealCompletenessUp$, $\LimitSelectorUp$, and $\RegularCauchyTailFiberUp$.
\end{proof}
