\section{The certificate}

\begin{definition}[Rat source specification]
\label{def:rat-source-specification}
The source is \(\IntUp \times \NatUp\) restricted to normalized denominator-positive pairs.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatSourceSpec}

\begin{theorem}[Rat source specification yields the carrier]
\label{thm:rat-source-spec-to-carrier}
A rational source witness determines a rational carrier witness: the numerator
is an integer carrier, the denominator is unary, and the positive one-tail
witness excludes internal sameness with \(\emp\).
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatSourceSpec\_to\_RatCarrier}
\begin{proof}
Unpack the source witness. The positive-denominator component gives a unary
tail \(t\) with \(d \hsame e_1(t)\). Unary closure under one-extension and
transport along \(\hsame\) give \(\mathsf{Unary}(d)\). If \(d\hsame \emp\),
then symmetry and transitivity give \(e_1(t)\hsame \emp\), contradicting
finite-kernel history no-confusion.
\end{proof}

\begin{definition}[Rat pattern specification]
\label{def:rat-pattern-specification}
The pattern is normalized numerator/denominator construction via a total normalization function on integer and positive-natural inputs.
\end{definition}

\begin{definition}[Rat classifier specification]
\label{def:rat-classifier-specification}
The classifier is structural sameness of normalized numerator and denominator representatives, tracked by mark sameness on signs and history sameness on the numerator and denominator histories.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatClassifierSpec}

\begin{theorem}[Rat classifier reflexivity]
\label{thm:rat-classifier-reflexivity}
Every rational carrier witness classifies its representative with itself.
\end{theorem}
\begin{proof}
Reuse the carrier witness for both endpoints. The sign component is witnessed by reflexivity of \(\msame\), and the numerator and denominator components are witnessed by reflexivity of \(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_refl}

\begin{theorem}[Rat classifier exposes positive denominators]
\label{thm:rat-classifier-positive-denominators}
If two rational representatives are related by the rational classifier, then
both endpoint denominators carry positive unary denominator witnesses.
\end{theorem}
\begin{proof}
Eliminate the classifier witness to expose the two endpoint rational carriers.
Apply the rational-carrier positive-denominator theorem to each endpoint
carrier.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_positive\_denominators}

\begin{theorem}[Rat classifier transports positive denominators]
\label{thm:rat-classifier-denominator-positive-transport}
If two rational representatives are related by the rational classifier, and
each denominator is related by \(\hsame\) to a displayed denominator history,
then both displayed denominator histories carry positive unary denominator
witnesses.
\end{theorem}
\begin{proof}
Eliminate the classifier witness to expose the two endpoint rational carriers.
Each endpoint carrier gives a positive unary denominator witness, and the two
denominator \(\hsame\) links transport those witnesses to the displayed
denominator histories.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_denominator\_positive\_transport}

\begin{theorem}[Rat positive denominator append factor or tail]
\label{thm:rat-positive-denominator-append-factor-or-tail}
If the append of two denominator histories carries a positive unary denominator
witness, then either the left factor already carries such a witness or the
right tail carries one.
\end{theorem}
\begin{proof}
Inspect the right tail. The empty case leaves the displayed append equal to the
left factor. A zero-headed tail contradicts the positive one-headed
denominator witness. For a one-headed tail, the positive witness exposes unary
membership of the appended core, and unary append factor recovery gives unary
membership of the right core, hence a positive denominator witness for the
tail.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_append\_factor\_or\_tail}

\begin{theorem}[Rat classifier denominator append closure]
\label{thm:rat-classifier-append-unary-denominators-closed}
If two rational representatives are classified the same, then appending
\(\hsame\)-matching unary histories to their denominators preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
Unpack the classifier witness into the two endpoint carriers and the sign,
numerator, and denominator sameness fields. Close both endpoint denominator
carriers under unary append, transporting the unary-tail witness along the
tail sameness for the second endpoint. The resulting denominator sameness follows by
eliminating the original denominator and tail sameness witnesses and applying
reflexivity to the resulting append history.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_append\_unary\_denominators\_closed}

\begin{theorem}[Rat classifier denominator prepend closure]
\label{thm:rat-classifier-prepend-unary-denominators-closed}
If two rational representatives are classified the same, then prepending
\(\hsame\)-matching unary histories to their denominators preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
Unpack the classifier witness into the two endpoint carriers and the sign,
numerator, and denominator sameness fields. Close both endpoint denominator
carriers under unary prepend, transporting unary membership of the first prefix
across prefix sameness for the second endpoint. The resulting denominator
sameness follows by eliminating the original denominator and prefix sameness
witnesses and applying reflexivity to the resulting append history.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_prepend\_unary\_denominators\_closed}

\begin{theorem}[Rat classifier unary denominator context closure]
\label{thm:rat-classifier-append-unary-denominator-context-closed}
If two rational representatives are classified the same, then surrounding their
denominators by $\hsame$-matching unary prefixes and unary tails preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
First apply denominator append closure to the classified representatives and
the matching unary tails. Then apply denominator prepend closure to the
resulting classified representatives and the matching unary prefixes. The sign
and numerator witnesses are unchanged, while the denominator endpoint relation
is obtained by the two concrete unary-context closure steps.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_append\_unary\_denominator\_context\_closed}

\begin{theorem}[Rat classifier append unary prefix denominator split]
\label{thm:rat-classifier-spec-append-unary-prefix-denominator-split}
If two rational representatives are classified after matching unary prefixes
are prepended to their denominators, then each displayed denominator side has a
positive unary witness either in its prefix or in its remaining denominator.
\end{theorem}
\begin{proof}
The classifier exposes positive unary denominator witnesses for the two
prefixed denominators. Transport unary membership across the prefix
\(\hsame\)-link, then split each prefixed denominator by the positive unary
left-split theorem.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_append\_unary\_prefix\_denominator\_split}

\begin{theorem}[Rat classifier transitivity]
\label{thm:rat-classifier-transitivity}
If one rational representative is classified the same as a second representative, and the second representative is classified the same as a third representative, then the first and third representatives are classified the same.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_trans}
\begin{proof}
Unpack both classifier witnesses. The endpoint carriers are preserved, while sign sameness and the two history-sameness components compose by the finite-kernel transitivity theorems for \(\msame\) and \(\hsame\).
\end{proof}

\begin{theorem}[Rat classifier symmetry]
\label{thm:rat-classifier-symmetry}
If one rational representative is classified the same as a second representative,
then the second representative is classified the same as the first.
\end{theorem}
\begin{proof}
Unpack the endpoint carriers and the sign, numerator, and denominator sameness
fields. Rebuild the classifier in the reverse direction using symmetry of
\(\msame\) for signs and symmetry of \(\hsame\) for both history components.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_symm}

\begin{theorem}[Rat classifier component transport]
\label{thm:rat-classifier-component-transport}
If both rational classifier endpoints are transported componentwise by
\(\msame\) on signs and \(\hsame\) on numerator and denominator histories,
then the rational classifier transports to the componentwise transported
representatives.
\end{theorem}
\begin{proof}
Unpack the rational classifier witness. Transport each endpoint rational
carrier by the component transport theorem, then compose the old sign,
numerator, and denominator sameness links with the reversed source endpoint
transports and the target endpoint transports.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_component\_transport}

\begin{theorem}[Rat history classifier one-tail exactness]
\label{thm:rat-history-classifier-e1-tail-unary-iff}
For denominator tails \(d,e:\mathsf{BHist}\), the rational history classifier
relates the one-extension denominators exactly when both tails are unary and
internally the same:
$$
\mathsf{RatHistoryClassifier}(\Eone(d),\Eone(e))
\Longleftrightarrow
\mathsf{Unary}(d)\land \mathsf{Unary}(e)\land \hsame(d,e).
$$
\end{theorem}
\begin{proof}
For the forward direction, unpack the classifier into two rational history
carrier witnesses and the endpoint \(\hsame\) link. The one-tail carrier
equivalence extracts unary membership of both tails, and \(\Eone\)-constructor
inversion gives \(\hsame(d,e)\). For the reverse direction, rebuild both
rational history carriers from the unary tails and lift \(\hsame(d,e)\) by
\(\Eone\)-congruence.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_e1\_tail\_unary\_iff}

\begin{theorem}[Rat history classifier exposes positive denominators]
\label{thm:rat-history-classifier-positive-denominators}
If denominator histories $d$ and $e$ are related by the rational history
classifier, then both $d$ and $e$ carry positive unary denominator witnesses.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into its two endpoint rational-history
carrier witnesses and the stored denominator $\hsame$ link. Convert each
endpoint carrier to a positive unary denominator witness by the rational history
carrier positive-denominator equivalence.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_positive\_denominators}

\begin{theorem}[Rat history classifier endpoints are nonempty]
\label{thm:rat-history-classifier-endpoints-not-empty}
If denominator histories $d$ and $e$ are related by the rational history
classifier, then neither endpoint is internally the same as the empty history:
$$
(\hsame(d,\emp)\to\mathsf{False})\land
(\hsame(e,\emp)\to\mathsf{False}).
$$
\end{theorem}
\begin{proof}
Unpack the rational history classifier into its two endpoint rational-history
carrier witnesses. Apply rational-history carrier nonemptiness to each endpoint
carrier.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_endpoints\_not\_empty}

\begin{theorem}[Rat history classifier zero-extension endpoint exclusion]
\label{thm:rat-history-classifier-zero-extension-endpoint-exclusion}
For histories $t,d:\mathsf{BHist}$, zero-extension cannot appear as either
endpoint of the rational history classifier:
$$
(\mathsf{RatHistoryClassifier}(\Ezero(t),d)\to\mathsf{False})\land
(\mathsf{RatHistoryClassifier}(d,\Ezero(t))\to\mathsf{False}).
$$
\end{theorem}
\begin{proof}
For the left endpoint, apply
\autoref{thm:rat-history-classifier-positive-denominators} to the classifier
hypothesis. Its first positive-denominator witness belongs to $\Ezero(t)$, so
\autoref{thm:rat-positive-denominator-e0-absurd} gives the contradiction.

For the right endpoint, apply
\autoref{thm:rat-history-classifier-positive-denominators} to the classifier
hypothesis again. Its second positive-denominator witness belongs to
$\Ezero(t)$, and
\autoref{thm:rat-positive-denominator-e0-absurd} rules out that endpoint.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_e0\_endpoint\_absurd}

The ten-field fit is: traditional target rational-denominator branch
exclusion; BEDC source $\mathsf{BHist}$ and
$\mathsf{RatHistoryClassifier}$; carrier $\mathsf{RatHistoryCarrier}$;
classifier $\mathsf{RatHistoryClassifier}$; stability from
positive-denominator readback; ledger the rejected zero head; core theorem
this block; exactness the two displayed contradictions; standard bridge
positive denominators are never zero-headed unary histories; status
$\mathsf{ProofTarget}$.
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_zero\_extension\_endpoint\_exclusion}

\begin{theorem}[Rat history classifier transitivity]
\label{thm:rat-history-classifier-trans}
If denominator histories $d$ and $e$ are related by the rational history
classifier, and $e$ and $f$ are related by the same classifier, then $d$ and
$f$ are related by the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the two rational history classifier witnesses. Keep the left endpoint
carrier from the first witness and the right endpoint carrier from the second
witness, then compose the denominator history sameness proofs by transitivity
of $\hsame$.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_trans}

\begin{theorem}[Rat history classifier endpoint transport]
\label{thm:rat-history-classifier-hsame-transport}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, and \(d\) and \(e\) are respectively internally the same as
\(d'\) and \(e'\), then \(d'\) and \(e'\) are related by the rational history
classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint rational-history carriers
and the stored \(\hsame(d,e)\) link. Transport both endpoint carriers across
the supplied history-sameness witnesses, then compose the reversed
\(\hsame(d,d')\) link, the stored classifier link, and \(\hsame(e,e')\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_hsame\_transport}

\begin{theorem}[Rat history classifier symmetry]
\label{thm:rat-history-classifier-symmetry}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, then \(e\) and \(d\) are related by the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier witness. Swap the two endpoint carrier
witnesses, and reverse the denominator history-sameness proof by symmetry of
\(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_symm}

\begin{theorem}[Rat history classifier unary denominator append closure]
\label{thm:rat-history-classifier-append-unary-denominator-closed}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, and unary tails \(t_d\) and \(t_e\) satisfy \(\hsame(t_d,t_e)\),
then appending the tails to the corresponding denominator histories preserves
the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint carriers and denominator
\(\hsame\). Close the left endpoint carrier under unary denominator append.
Transport unary membership from \(t_d\) to \(t_e\), close the right endpoint
carrier under append, and combine the denominator \(\hsame\) with the tail
\(\hsame\) by constructor cases on append.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_append\_unary\_denominator\_closed}

\begin{theorem}[Rat history classifier unary denominator prepend closure]
\label{thm:rat-history-classifier-prepend-unary-denominator-closed}
If denominator histories $d$ and $e$ are related by the rational history
classifier, and unary prefixes $p_d$ and $p_e$ satisfy $\hsame(p_d,p_e)$, then
prepending the prefixes to the corresponding denominator histories preserves the
rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint carriers and denominator
$\hsame$. Close the left endpoint carrier under unary denominator prepend.
Transport unary membership from $p_d$ to $p_e$, close the right endpoint carrier
under prepend, and combine the denominator and prefix $\hsame$ witnesses by
constructor cases on the continuation append operation.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_prepend\_unary\_denominator\_closed}

\begin{theorem}[Rat history classifier unary denominator context closure]
\label{thm:rat-history-classifier-unary-denominator-context-closed}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, unary prefixes \(p_d,p_e\) satisfy \(\hsame(p_d,p_e)\), and unary
tails \(t_d,t_e\) satisfy \(\hsame(t_d,t_e)\), then placing the matching prefix
and tail around the corresponding denominators preserves the rational history
classifier.
\end{theorem}
\begin{proof}
First apply unary denominator append closure to the classified denominator
histories and the matching tails. Then apply unary denominator prepend closure
to the resulting classified denominator histories and the matching prefixes.
The endpoint carrier witnesses are closed by the two concrete unary closure
steps, and the denominator relation is the composed \(\hsame\)-respecting
append context.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_unary\_denominator\_context\_closed}

\begin{theorem}[Rat history classifier unary denominator context positive denominators]
\label{thm:rat-history-classifier-unary-denominator-context-positive-denominators}
If a rational history classifier is closed under matching unary denominator
prefixes and tails, then the two contextual denominator endpoints have positive
unary denominator witnesses.
\end{theorem}
\begin{proof}
Apply \autoref{thm:rat-history-classifier-unary-denominator-context-closed}
to the original classifier and the matching unary contexts. Then apply
\autoref{thm:rat-history-classifier-positive-denominators} to the resulting
contextual classifier.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_unary\_denominator\_context\_positive\_denominators}

\begin{theorem}[Rat history classifier unary context zero-extension endpoint exclusion]
\label{thm:rat-history-classifier-unary-context-zero-extension-endpoint-exclusion}
Let $d,e,p_d,p_e,t_d,t_e,z,z':\mathsf{BHist}$. If
$\mathsf{RatHistoryClassifier}(d,e)$ holds, $p_d,p_e$ are unary prefixes with
$\hsame(p_d,p_e)$, and $t_d,t_e$ are unary tails with $\hsame(t_d,t_e)$, then
the two contextual denominator endpoints cannot be internally the same as
zero-extension histories:
$$
(\hsame(\mathsf{append}(p_d,\mathsf{append}(d,t_d)),\Ezero(z))\to
\mathsf{False})\land
(\hsame(\mathsf{append}(p_e,\mathsf{append}(e,t_e)),\Ezero(z'))\to
\mathsf{False}).
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:rat-history-classifier-unary-denominator-context-positive-denominators}
to the displayed classifier, the matching unary prefix context, and the
matching unary tail context. This produces positive unary denominator witnesses
for $\mathsf{append}(p_d,\mathsf{append}(d,t_d))$ and
$\mathsf{append}(p_e,\mathsf{append}(e,t_e))$.

For the left endpoint, transport the positive unary denominator witness across
the displayed $\hsame$ link from
$\mathsf{append}(p_d,\mathsf{append}(d,t_d))$ to $\Ezero(z)$. Then apply
\autoref{thm:rat-positive-denominator-e0-absurd} to rule out that
zero-extension endpoint.

For the right endpoint, repeat the same transport across the displayed
$\hsame$ link from $\mathsf{append}(p_e,\mathsf{append}(e,t_e))$ to
$\Ezero(z')$. The positive-denominator zero-head absurdity theorem gives the
second contradiction.
\end{proof}

The ten-field fit is: traditional target contextual positive-rational branch
exclusion; BEDC source $\mathsf{RatHistoryClassifier}$ over $\mathsf{BHist}$;
carrier $\mathsf{RatHistoryCarrier}$; classifier
$\mathsf{RatHistoryClassifier}$; stability from unary context closure and
positive-denominator transport; ledger the hidden prefix and tail contexts;
core theorem this block; exactness the two contradictions; downstream consumer
$\mathsf{FieldUp}(\mathsf{RatUp})$ denominator continuation and
$\mathsf{RealUp}$ stream-prefix readback; status $\mathsf{ProofTarget}$.

\begin{theorem}[Rat history classifier context one-tail pair readback]
\label{thm:rat-history-classifier-unary-context-e1-pair-readback}
If a rational history classifier is closed under matching unary denominator prefixes and tails, and the resulting left and right endpoints display as one-extension histories, then the displayed tails are unary and internally the same.
\end{theorem}
\begin{proof}
Apply rational history classifier unary denominator context closure to the original classified denominators and the matching unary contexts. Transport the closed classifier across the two displayed endpoint sameness witnesses, then use rational one-tail classifier exactness to read back the two unary tails and their $\hsame$ relation.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_unary\_context\_e1\_pair\_readback}

\begin{theorem}[Rat history classifier continuation context one-tail pair readback]
\label{thm:rat-history-classifier-cont-unary-context-e1-pair-readback}
If the matching unary denominator context is presented by continuation
displays and the two outputs are one-extension histories, then their tails are
unary and internally the same.
\end{theorem}
\begin{proof}
Use the two continuation displays and append associativity to identify the
outputs with the normal context endpoints, then apply
\autoref{thm:rat-history-classifier-unary-context-e1-pair-readback}.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_cont\_unary\_context\_e1\_pair\_readback}
