\begin{theorem}[Real unary StreamNameUp classifier selected endpoint shape package]
\label{thm:real-unary-streamname-classifier-selected-endpoint-shape-package}
For unary observation maps $s,t,s',t':\Hist\to\Hist$, a certified observation
$n:\Hist$, and histories $a,b,z_s,z_t:\Hist$, assume
$$
\mathsf{RatStreamNameClassifier}(s,t),\quad
\mathsf{UnaryHistory}(n),
$$
the pointwise transport rows
$$
\forall k,\ \mathsf{UnaryHistory}(k)\to\hsame(s(k),s'(k)),
\quad
\forall k,\ \mathsf{UnaryHistory}(k)\to\hsame(t(k),t'(k)),
$$
and the displayed selected endpoints
$$
\hsame(s'(n),\Eone(a)),\quad \hsame(t'(n),\Eone(b)).
$$
Then pointwise transport carries the StreamNameUp classifier to the transported
maps, and the selected endpoints obtained from that classifier carry the full
RatUp denominator and one-tail shape package:
$$
\begin{array}{l}
\mathsf{RatStreamNameClassifier}(s',t')\land\\
\mathsf{RatHistoryClassifier}(s'(n),t'(n))\land
\mathsf{PositiveUnaryDenominator}(s'(n))\land
\mathsf{PositiveUnaryDenominator}(t'(n))\land\\
\mathsf{UnaryHistory}(s'(n))\land
\mathsf{UnaryHistory}(t'(n))\land
(\hsame(s'(n),\emp)\to\mathsf{False})\land
(\hsame(t'(n),\emp)\to\mathsf{False})\land\\
(\hsame(s'(n),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t'(n),\Ezero(z_t))\to\mathsf{False})\land\\
\mathsf{UnaryHistory}(a)\land
\mathsf{UnaryHistory}(b)\land
\hsame(a,b).
\end{array}
$$
\end{theorem}
\begin{proof}
First convert the StreamNameUp classifier into the Real unary classifier. Apply
\autoref{thm:real-unary-streamname-classifier-exactness} with the two carrier
fields projected from $\mathsf{RatStreamNameClassifier}(s,t)$, then use the
reverse implication on the same classifier row.

Next apply \autoref{thm:real-unary-streamname-transported-classifier} to the
same two carrier fields, the converted Real unary classifier, and the two
pointwise transport rows. This gives
$\mathsf{RatStreamNameClassifier}(s',t')$.

Now apply
\autoref{thm:real-unary-streamname-transported-selected-endpoint-shape-package}
to that Real unary classifier, the selected certified observation $n$, the two
pointwise transport rows, and the two displayed $\Eone$ endpoint comparisons.
The conclusion is exactly the displayed selected endpoint package. Repack it
with the transported StreamNameUp classifier row.
\end{proof}

Fit. Traditional target: selected unary stream observation readback from a
certified StreamNameUp classifier. BEDC source: $\StreamNameUp+\RealUp+\RatUp$
over $\mathsf{BHist}$. Carrier: $\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ transported through
$\mathsf{RealUnaryStreamClassifier}$. Ledger: selected unary observation and
endpoint displays. Core theorem:
\autoref{thm:real-unary-streamname-classifier-selected-endpoint-shape-package}.
Exactness: transported StreamNameUp classifier and displayed selected endpoint
package. Standard bridge: pointwise rational stream observation readback.
Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp classifier selected endpoint tail pairwise coherence]
\label{thm:real-unary-streamname-classifier-selected-endpoint-tail-pairwise-coherence}
For unary observation maps $s,t,s',t':\Hist\to\Hist$, a certified observation
$n:\Hist$, and histories $a,a',b,b':\Hist$, assume
$\mathsf{RatStreamNameClassifier}(s,t)$, $\mathsf{UnaryHistory}(n)$, the two
pointwise transport rows of
\autoref{thm:real-unary-streamname-classifier-selected-endpoint-shape-package},
and the four displayed endpoints
$$
\hsame(s'(n),\Eone(a)),\quad \hsame(s'(n),\Eone(a')),\quad
\hsame(t'(n),\Eone(b)),\quad \hsame(t'(n),\Eone(b')).
$$
Then $\mathsf{UnaryHistory}(a)$, $\mathsf{UnaryHistory}(a')$,
$\mathsf{UnaryHistory}(b)$, $\mathsf{UnaryHistory}(b')$, and all six tail
comparisons hold:
$$
\hsame(a,a'),\quad \hsame(a,b),\quad \hsame(a,b'),\quad
\hsame(a',b),\quad \hsame(a',b'),\quad \hsame(b,b').
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-classifier-selected-endpoint-shape-package}
twice, first to the displayed pair $(a,b)$ and then to $(a',b')$, instantiating
the zero-headed display parameters by endpoint tails. This supplies the four
unary-history rows together with $\hsame(a,b)$ and $\hsame(a',b')$.

For the same-side comparisons, compose the two displays of $s'(n)$ to obtain
$\hsame(\Eone(a),\Eone(a'))$ and use
$\mathsf{BEDC.FKernel.Hist.hsame\_e1\_inversion\_iff}$ to read back
$\hsame(a,a')$. The same composition and e-one inversion applied to the two
displays of $t'(n)$ gives $\hsame(b,b')$.

It remains to fill the two mixed comparisons. Compose $\hsame(a,b)$ with
$\hsame(b,b')$ by $\mathsf{BEDC.FKernel.Hist.hsame\_trans}$ to obtain
$\hsame(a,b')$; compose the symmetry of $\hsame(a,a')$ with $\hsame(a,b)$ to
obtain $\hsame(a',b)$. Package the four unary rows and the six comparisons.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RatStreamNameClassifier\_selected\_endpoint\_tail\_pairwise\_coherence}

Fit. Traditional target: selected unary stream observation readback. BEDC source:
RealUp unary streams plus RatUp classifier. Carrier: unary-indexed rational
observation maps. Classifier: $\mathsf{RealUnaryStreamClassifier}$. Stability:
pointwise $\hsame$ transport. Ledger: selected certified observation and endpoint
displays. Core theorem:
\autoref{thm:real-unary-streamname-transported-selected-endpoint-shape-package}.
Exactness: displayed endpoint package. Standard bridge: selected rational
observation readback for RealUp names. Status: $\mathsf{ProofTarget}$.
