\begin{definition}[CauchyFilterCompletion root unblock carrier]
\label{def:cauchy-filter-completion-root-unblock-carrier}
The root-unblock carrier for $\CauchyFilterCompletionUp$ is the same finite packet
$$
F=(C,W,T,R,L,H,K,P,N)
$$
read with the following obligation order: the $\CauchyFilterUp/\FilterBaseUp$ source row $C$, the finite $\StreamNameUp$ windows $W$, the $\DyadicRatCoreUp$ tolerance ledger $T$, the $\RegSeqRatUp$ readback row $R$, the terminal $\RealUp$ seal $L$, componentwise $\BHist/\hsame$ transport $H$, displayed $\Cont$ replay $K$, $\Pkg$ provenance $P$, and the local $\NameCert_{\CauchyFilterCompletionUp}$ row $N$. A root consumer receives no quotient filter, selected limit, host real equality, countable-choice selector, ambient completeness theorem, or detached $\MetricCompletionUp/\UniformCompletionUp$ carrier.
\end{definition}

\begin{theorem}[CauchyFilterCompletion root window exposure]
\label{thm:cauchy-filter-completion-root-unblock-window}
Every completion-facing read of a root-unblock carrier $F=(C,W,T,R,L,H,K,P,N)$ opens the displayed $\CauchyFilterUp/\FilterBaseUp$ source row $C$ and the finite $\StreamNameUp$ window row $W$ before it consumes the $\DyadicRatCoreUp$ tolerance ledger $T$ or the $\RegSeqRatUp$ readback row $R$.
\end{theorem}
\begin{proof}
Project the root-unblock carrier of \autoref{def:cauchy-filter-completion-root-unblock-carrier}. Its first completion-facing coordinates are the source row $C$, window row $W$, tolerance row $T$, and readback row $R$.

Apply \autoref{thm:cauchy-filter-completion-observation-base}. It forces every accepted completion read to start from the displayed source row before any window, tolerance, readback, or seal row is available.

Use \autoref{thm:cauchy-filter-completion-window-tolerance-exactness}. Once $C$ and $W$ are open, the matching tolerance row $T$ is required before $R$ can be consumed, so the read cannot start from a detached regular sequence.
\end{proof}
\leanchecked{BEDC.Derived.CauchyfiltercompletionUp.CauchyFilterCompletionRootWindowExposure}

\begin{theorem}[CauchyFilterCompletion root Real seal route]
\label{thm:cauchy-filter-completion-root-unblock-real-seal}
Every $\RealUp$ seal read of a root-unblock carrier is downstream of the same source, window, tolerance, and readback rows:
$$
C,W,T,R \longmapsto L \longmapsto H,K,P,N .
$$
The seal route exports no quotient filter, selected limit, host equality, countable choice, ambient completeness, or detached completion object.
\end{theorem}
\begin{proof}
Start with \autoref{thm:cauchy-filter-completion-root-unblock-window}. It exposes $C,W,T,R$ before the terminal seal can be inspected by a completion-facing consumer.

Apply \autoref{thm:cauchy-filter-completion-real-seal-refusal}. The $\RealUp$ seal $L$ exports only the finite route already displayed by the packet and refuses quotient, selector, host-equality, choice, completeness, and detached-completion exits.

Finally preserve the route through $H,K,P,N$. These rows transport, replay, source, and name the same packet, so none of them can replace the source-window-readback chain.
\end{proof}

\begin{theorem}[CauchyFilterCompletion root uniform route]
\label{thm:cauchy-filter-completion-root-unblock-uniform-route}
Every $\UniformCompletionUp$ or $\MetricCompletionUp$ consumer of a root-unblock carrier receives only the displayed route
$$
C,W,T,R,L,H,K,P,N .
$$
Uniform and metric completion reads may inspect the provenance row, but they cannot introduce a second completion carrier, quotient filter, selected limit, host equality, countable choice, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-filter-completion-root-unblock-carrier}. The only completion-facing rows available to a consumer are $C,W,T,R,L,H,K,P,N$.

Use \autoref{thm:cauchy-filter-completion-metric-uniform-compatibility}. It states that $\MetricCompletionUp$ and $\UniformCompletionUp$ consumers read the same finite completion route and cannot replace it by detached completion data.

Apply \autoref{thm:cauchy-filter-completion-root-unblock-real-seal}. The terminal Real seal is already downstream of the source, window, tolerance, and readback rows, so uniform and metric consumers inherit the same displayed boundary.
\end{proof}

\begin{theorem}[CauchyFilterCompletion root NameCert surface]
\label{thm:cauchy-filter-completion-root-unblock-namecert}
The root obligation surface of $\CauchyFilterCompletionUp$ is exactly the root-unblock carrier of \autoref{def:cauchy-filter-completion-root-unblock-carrier} together with the window exposure of \autoref{thm:cauchy-filter-completion-root-unblock-window}, the Real seal route of \autoref{thm:cauchy-filter-completion-root-unblock-real-seal}, and the metric-uniform route of \autoref{thm:cauchy-filter-completion-root-unblock-uniform-route}. A root consumer must therefore read the displayed $\CauchyFilterUp$, $\FilterBaseUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\UniformCompletionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows before exporting any completion-facing result.
\end{theorem}
\begin{proof}
Combine the three root routes. The window theorem exposes the source and finite observation rows, the Real seal theorem fixes the terminal readback route, and the metric-uniform theorem keeps completion consumers on the same displayed carrier.

Now apply \autoref{thm:cauchy-filter-completion-carrier-ledger-package}. It identifies the local NameCert package with the carrier rows and ledger refusals over $C,W,T,R,L,H,K,P,N$.

Finally use \autoref{thm:cauchy-filter-completion-completion-scope}. The chapter closes only this finite completion route and refuses quotient filters, selected limits, host real equality, countable-choice selectors, ambient completeness, and detached completion objects.
\end{proof}

\begin{theorem}[CauchyFilterCompletion root Cauchy-filter limit existence]
\label{thm:cauchy-filter-completion-root-cauchy-filter-limit-existence}
Every completion-facing consumer of a root-unblock carrier that claims a Cauchy-filter limit must display the finite route
$$
C,W,T,R,L,H,K,P,N .
$$
The limit obligation is therefore carried by the $\CauchyFilterUp/\FilterBaseUp$ source row $C$, the $\StreamNameUp$ windows $W$, the $\DyadicRatCoreUp$ tolerance ledger $T$, the $\RegSeqRatUp$ readback $R$, the terminal $\RealUp$ seal $L$, and the structural $\BHist/\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It is not a selected filter limit, quotient representative, host real equality proof, countable-choice selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start from the root-unblock carrier. The displayed tuple contains only the rows $C,W,T,R,L,H,K,P,N$, so any asserted Cauchy-filter limit must be read through those coordinates.

Apply the root window exposure theorem to force the source and finite windows before tolerance and readback. Apply the root Real seal route to put the terminal seal downstream of that same source-window-readback path.

The NameCert surface then packages the route as a finite obligation. Since the packet has no coordinate for quotient representatives or selected limits, the existence readback is the displayed completion route itself, not an external completeness principle.
\end{proof}

\begin{theorem}[CauchyFilterCompletion uniform-completion universal property]
\label{thm:cauchy-filter-completion-uniform-completion-universal-property}
Every $\UniformCompletionUp$ consumer of a root-unblock carrier factors its universal-completion obligation through the same finite rows
$$
C,W,T,R,L,H,K,P,N .
$$
The universal property can use the $\CauchyFilterUp$ source, $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, $\BHist/\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming, but it cannot use quotient filter representatives, selected limits, detached uniform-completion carriers, host equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project the root-unblock carrier. The only uniform-facing coordinate beyond the source, windows, tolerance, readback, and Real seal is the provenance row $P$.

Apply the root uniform route. It identifies every $\UniformCompletionUp$ or $\MetricCompletionUp$ consumer with the displayed packet route and blocks detached completion data.

The universal property is therefore stated over the same finite route. Transport through $H$, replay through $K$, provenance through $P$, and local naming through $N$ preserve the packet; none of those rows creates quotient representatives, selected limits, host equality, choice, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyFilterCompletion Real seal uniqueness interface]
\label{thm:cauchy-filter-completion-real-seal-uniqueness-interface}
Any two root-unblock consumers that read the same displayed $\CauchyFilterUp/\FilterBaseUp$ row $C$, $\StreamNameUp$ windows $W$, $\DyadicRatCoreUp$ tolerance ledger $T$, and $\RegSeqRatUp$ readback $R$ reach the same $\RealUp$ seal interface $L$ inside the accepted packet. The interface is transported only by $H$, replayed only by $K$, sourced only by $P$, and named only by $N$.
\end{theorem}
\begin{proof}
Use the root window exposure theorem for both consumers. Once $C,W,T,R$ are fixed, neither consumer has another source, window, tolerance, or readback coordinate available inside the carrier.

Apply the root Real seal route. The only terminal Real-facing row downstream of $C,W,T,R$ is $L$.

Finally apply the root NameCert surface. The structural rows $H,K,P,N$ preserve, replay, source, and name the same interface, so the comparison cannot escape to quotient filter equality, selected limits, host equality, countable choice, ambient completeness, or detached completion objects.
\end{proof}

\begin{closurestatus}{\CauchyFilterCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-filter-completion-carrier}, \autoref{thm:cauchy-filter-completion-namecert-obligations}, \autoref{thm:cauchy-filter-completion-real-seal-handoff}, and \autoref{thm:cauchy-filter-completion-located-uniform-gluing} seed the finite Cauchy-filter completion boundary between saturated filter data, located-filter reads, uniform-filter handoffs, and the downstream $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected limits, host real equality, countable-choice selectors, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires carrier admission, tolerance exactness, Real seal handoff, uniform-completion provenance, and ledger refusal proofs for the same packet.}
  \constructivestory{A $\CauchyFilterCompletionUp$ packet is generated from a CauchyFilter row, finite StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a RealUp seal handoff, componentwise transport, continuation replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
