\chapter{A Concrete Naming Certificate for $\FrechetKolmogorovCompactnessUp$}
\label{ch:concrete-instances-frechet-kolmogorov-compactness-namecert}
\origin{human}

Following Kolmogorov--Riesz and Frechet compactness in constructive finite-window form, the $\FrechetKolmogorovCompactnessUp$ packet records the BEDC route by which compact metric control, total boundedness, uniform equicontinuity, completion readiness, and terminal Real readbacks are named as one compactness-facing criterion. It sits after the compact-metric surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the total-bounded source of \autoref{ch:concrete-instances-totallybounded-namecert}, the uniform-equicontinuity modulus of \autoref{ch:concrete-instances-uniform-equicontinuity-modulus-namecert}, the complete-metric handoff of \autoref{ch:concrete-instances-completemetric-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The carrier names finite net and completion rows only; it does not assert open-cover compactness, choose subsequences, select subcovers, or import ambient completeness outside the displayed packet.

\begin{definition}[Frechet-Kolmogorov compactness carrier]
\label{def:frechet-kolmogorov-compactness-carrier}
A $\FrechetKolmogorovCompactnessUp$ carrier is a finite $\BHist$ packet
$$
K=(M,T,E,Q,C,S,R,H,A,P,N)
$$
with the following rows:
\begin{enumerate}
\item $M$ is the $\CompactMetricUp$ source row exposing the displayed metric and compactness-facing finite-net interface.
\item $T$ is the $\TotallyBoundedUp$ row recording the finite $\varepsilon$-net budget consumed by the criterion.
\item $E$ is the $\UniformEquicontinuityModulusUp$ row binding a shared modulus to the same finite windows.
\item $Q$ is the $\CompleteMetricUp$ completion boundary row, used only after the finite net and modulus rows are visible.
\item $C$ is the compactness-criterion row relating the metric, total-bounded, equicontinuity, and completion rows as one finite BEDC route.
\item $S$ is the $\StreamNameUp$ window ledger for the inspected net cells, modulus requests, and Cauchy-readback windows.
\item $R$ is the $\RegSeqRatUp$ readback row for rational tolerance comparisons.
\item $H$ records componentwise $\hsame$ transport for all displayed source, net, modulus, completion, readback, and naming rows.
\item $A$ records displayed $\Cont$ replay of the same finite route.
\item $P$ is the $\Pkg$ provenance over $\FrechetKolmogorovCompactnessUp$, $\CompactMetricUp$, $\TotallyBoundedUp$, $\UniformEquicontinuityModulusUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FrechetKolmogorovCompactnessUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $M,T,E,Q,C,S,R,H,A,P,N$. It has no coordinate for an open-cover compactness theorem, selected subsequence, selected subcover, quotient completion equality, countable-choice schedule, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Frechet-Kolmogorov compactness NameCert obligations]
\label{thm:frechet-kolmogorov-compactness-namecert-obligations}
For every accepted $\FrechetKolmogorovCompactnessUp$ carrier $K=(M,T,E,Q,C,S,R,H,A,P,N)$, the local $\NameCert_{\FrechetKolmogorovCompactnessUp}$ surface consists exactly of compact-metric source exposure through $M$; total-bounded finite-net exposure through $T$; uniform-modulus exposure through $E$; completion-boundary exposure through $Q$; criterion compatibility through $C$; finite-window and rational readback exposure through $S,R$; componentwise transport through $H$; displayed replay through $A$; provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The coordinates are precisely the compact-metric source, total-bounded net, uniform-modulus, completion-boundary, criterion, finite-window, readback, transport, replay, provenance, and naming rows.

Read the source rows in order. The compact-metric row gives the metric-facing carrier; the total-bounded row supplies finite nets over that metric; the uniform-equicontinuity row uses the same windows; and the completion row is reached only through those displayed finite controls.

The structural rows $H,A,P,N$ transport, replay, source, and name that same route. Since no carrier coordinate names a selected subsequence, selected subcover, open-cover compactness proof, quotient equality, or ambient completeness theorem, the listed rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Frechet-Kolmogorov compactness total-bounded handoff]
\label{thm:frechet-kolmogorov-compactness-total-bounded-handoff}
Every compactness-facing consumer of an accepted $\FrechetKolmogorovCompactnessUp$ carrier must read the total-bounded row $T$ through the compact-metric source $M$ and the uniform-modulus row $E$ before it inspects the StreamName and RegSeqRat readback rows $S,R$. Thus finite-net evidence is exported as a displayed BEDC handoff, not as a choice-selected dense set or an unrecorded cover refinement.
\end{theorem}
\begin{proof}
Begin with the compact-metric source row. It fixes the metric and the carrier surface on which the total-bounded net is meaningful.

The total-bounded row then exposes the finite net budget, while the uniform-modulus row forces all later compactness requests to use the same finite tolerance windows. Only after those rows are visible can the StreamName and RegSeqRat rows read the inspected windows and rational tolerances.

Therefore the consumer receives a finite-net handoff through $M,T,E,S,R$ and not a selected dense subset, a selected subcover, or an unrecorded refinement outside the packet.
\end{proof}

\begin{theorem}[Frechet-Kolmogorov compactness completion boundary]
\label{thm:frechet-kolmogorov-compactness-completion-boundary}
The completion-facing part of an accepted $\FrechetKolmogorovCompactnessUp$ carrier is confined to the displayed row $Q$ after the compact-metric source, total-bounded net, and uniform-modulus rows have been read. It may hand a downstream completion consumer a finite Cauchy-window boundary, but it does not claim quotient completion equality, a selected limit representative, sequential compactness, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the route through $M,T,E$ first. These rows supply the metric source, finite-net budget, and shared modulus required before any completion boundary can be inspected.

The completion row $Q$ is therefore a boundary row over already displayed finite data. The readback rows $S,R$ and the structural rows $H,A,P,N$ keep the same route visible under windowing, rational comparison, transport, replay, provenance, and naming.

Because the carrier contains no quotient-equality, selected-limit, sequential-compactness, open-cover, or ambient-completeness coordinate, a completion consumer cannot obtain any of those objects from the local packet.
\end{proof}

\closureat{FrechetKolmogorovCompactnessUp}{seedStr}

\begin{closurestatus}{\FrechetKolmogorovCompactnessUp}
  \constructivestory{A $\FrechetKolmogorovCompactnessUp$ packet is generated from a CompactMetric source row, a TotallyBounded finite-net row, a UniformEquicontinuityModulus row, a CompleteMetric boundary row, StreamName finite windows, RegSeqRat readback, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:frechet-kolmogorov-compactness-carrier}, \autoref{thm:frechet-kolmogorov-compactness-namecert-obligations}, \autoref{thm:frechet-kolmogorov-compactness-total-bounded-handoff}, and \autoref{thm:frechet-kolmogorov-compactness-completion-boundary} seed the finite compactness criterion over compact-metric, total-bounded, uniform-modulus, completion-boundary, StreamName, RegSeqRat, Real, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, sequential compactness, selected subsequences, selected subcovers, quotient completion equality, countable choice, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net exposure, uniform-modulus compatibility, completion-boundary nonescape, readback stability, transport, replay, provenance, and local naming for BEDC.Derived.FrechetKolmogorovCompactnessUp.}
\end{closurestatus}
