\begin{theorem}[CauchyCriterion StreamName Real budget-selector boundary]
\label{thm:cauchycriterion-streamname-real-budget-selector-boundary}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet. Any
$\RealUp$-completion consumer or finite-window budget selector sharing the
displayed
$$
\StreamNameUp,\quad \RegSeqRatUp,\quad \DyadicRatCoreUp,\quad \RealUp
$$
rows must read through the CauchyCriterion route
$$
M,\quad Q,\quad T,\quad W,\quad E,\quad H,\quad C,\quad P,\quad N
$$
before exposing a selector output. Conversely, a selector that displays this
route has exactly the finite CauchyCriterion budget surface available for the
shared StreamName--RegSeqRat--DyadicRatCore--Real read.

The boundary exports no quotient stream, selected limit, host real equality,
ambient completeness principle, unrecorded completion object, or selector
choice independent of $M,Q,T,W,E,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_streamname\_real\_budget\_selector\_boundary}
\begin{proof}
Start with the CauchyCriterion handoff
\autoref{thm:cauchycriterion-regseqrat-streamname-realup-handoff}. It places
the $\StreamNameUp$ finite window, the $\RegSeqRatUp$ source row, the
$\DyadicRatCoreUp$ budget rows, and the $\RealUp$ seal on the displayed
CauchyCriterion carrier rows.

Next apply the completion boundary
\autoref{thm:cauchycriterion-tail-budget-real-completion-boundary}. It says
that any $\CompletionUp$ or $\RealCauchyCompletionUp$ consumer sharing those
four faces must factor through $M,Q,T,W,E,H,C,P,N$ before it can read a
completion seal.

Now use the finite-window selector surfaces from the StreamName and Real
siblings. The request and coverage theorems
\autoref{thm:streamname-tail-compatible-window-request} and
\autoref{thm:streamname-tail-compatible-window-coverage} identify a
finite-window selector by its selected observation, bundle membership,
tail-selector route, finite budget surface, pointwise $\RegSeqRatUp$ handoff,
and the support rows $\hsame,\Cont,\Pkg,\NameCert$. The budget handoff
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff} and the
boundary \autoref{thm:streamname-realup-finite-window-seal-boundary} then
force the $\RealUp$ read to use the same finite surface.

Finally read the completion-facing exit through
\autoref{thm:streamname-real-completion-four-object-exit-route}. Its four
faces are exactly $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$, with no fifth completion coordinate. Combining this exit route with
the CauchyCriterion handoff and tail-budget boundary gives the stated
factorization before any selector output is exposed, and the excluded objects
have no row in the resulting packet.
\end{proof}

\begin{theorem}[CauchyCriterion finite-request section return]
\label{thm:cauchycriterion-finite-request-section-return}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet whose
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$
rows agree with a public finite request section. Then the selector-seal route
of $K$ returns exactly the $\StreamNameUp$ finite-request section before any
$\RealUp$ seal is exposed.

Conversely, the displayed finite request section determines the
$\CauchyCriterionUp$ selector budget surface over the same $M,Q,T,W,E,H,C,P,N$
rows. The return route exports no quotient stream, selected limit, host real
equality, countable-choice selector, ambient completeness principle, or second
seal source.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_finite\_request\_section\_return}
\begin{proof}
First apply
\autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. It
places the selector-facing read on the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows before
any selector output or $\RealUp$ seal can be consumed.

Next use
\autoref{thm:cauchycriterion-uniform-selector-seal-compatibility} and
\autoref{thm:cauchycriterion-selector-seal-route-pullback}. These results put
the selector route and its seal-facing pullback on the same finite structural
surface carried by $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

For the return direction, read the StreamName and Real finite-request locks.
The StreamName terminality rows identify the finite request section by the
selected window, bundle membership, tail-selector route, pointwise
$\RegSeqRatUp$ handoff, and support rows; the $\RealUp$ finite-request fusion
and seal lock then force the seal-facing consumer to reuse that same section.

Finally apply
\autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}. The
synchronizer is total on the common finite packet, so the CauchyCriterion
selector budget surface is determined by the displayed section and cannot
escape to quotient streams, selected limits, host real equality, countable
choice, ambient completeness, or a second seal source.
\end{proof}

\begin{theorem}[CauchyCriterion uniform selector-seal compatibility]
\label{thm:cauchycriterion-uniform-selector-seal-compatibility}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and
let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted
$\UniformCauchyCriterionUp$ packet. Suppose the two presentations display the
same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ finite
rows at the completion-facing boundary. Then the budget-selector output of the
$\CauchyCriterionUp$ route and the shared-threshold seal output of the
$\UniformCauchyCriterionUp$ route factor through the same finite packet before
any $\RealUp$ seal is exposed.

The common packet is the displayed StreamName--RegSeqRat--DyadicRatCore--Real
surface with its $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support
rows. It contains no quotient stream, selected limit, host real equality,
detached family threshold, ambient completeness principle, or second
completion seal.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_uniform\_selector\_seal\_compatibility}
\begin{proof}
Begin with the CauchyCriterion side. Apply
\autoref{thm:cauchycriterion-regseqrat-streamname-realup-handoff} and
\autoref{thm:cauchycriterion-tail-budget-real-completion-boundary}. These
place the selector-facing read on the displayed $M,Q,T,W,E,H,C,P,N$ packet
before any Real or Completion seal can be consumed.

Next expose the StreamName exit route. The finite-window request and coverage
rows, together with
\autoref{thm:streamname-real-regseq-finite-window-budget-handoff},
\autoref{thm:streamname-realup-finite-window-seal-boundary}, and
\autoref{thm:streamname-real-completion-four-object-exit-route}, identify the
four public faces as $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\RealUp$ with no fifth completion coordinate.

Now read the uniform presentation. Apply
\autoref{thm:uniform-cauchy-criterion-shared-threshold-transport}. The family
threshold request is transported as one finite route through the displayed
window, threshold, tolerance, and tail rows, with the support rows supplied by
$H_U,C_U,P_U,N_U$.

Finally apply
\autoref{thm:uniform-cauchy-criterion-real-seal-handoff},
\autoref{thm:uniform-cauchy-criterion-real-seal-consumer-factorization}, and
\autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. The uniform seal
is downstream of the same finite packet, and the non-escape boundary removes
quotient streams, selected limits, host equality, detached thresholds, ambient
completeness, and any second completion seal. Hence the selector route and the
shared-threshold seal route agree on the finite packet before the $\RealUp$
seal is exposed.
\end{proof}

\begin{theorem}[CauchyCriterion selector-seal route pullback]
\label{thm:cauchycriterion-selector-seal-route-pullback}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and
let $D=(B_D,T_D,W_D,R_D,L_D,H_D,C_D,P_D,N_D)$ be an accepted
$\DiagonalLimitCompatibilityUp$ root formal source. Suppose the two packets
share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and
$\RealUp$ rows at the selector-seal boundary. Then the
$\CauchyCriterionUp$ selector-seal route is the pullback of the diagonal root
formal route along the structural rows
$$
\hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

The resulting route is exactly the common StreamName--RegSeqRat--DyadicRatCore--Real
surface with its structural support rows. It exports no quotient stream,
selected limit, host real equality, countable-choice selector, ambient
completeness principle, or second seal source.
\end{theorem}
\begin{proof}
Begin with the CauchyCriterion boundary
\autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. It
forces every selector-facing read through the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows before
any selector output is exposed.

Next use the uniform selector-seal compatibility of
\autoref{thm:cauchycriterion-uniform-selector-seal-compatibility}. This places
the selector route on the same finite structural surface carried by
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, with no extra completion-facing
coordinate.

Now read the diagonal root formal source through
\autoref{def:diagonal-limit-compatibility-root-formal-source} and
\autoref{thm:diagonal-limit-compatibility-root-formal-route}. The root route
displays the finite source rows and consumes its support rows in the same
structural order.

Finally apply
\autoref{thm:diagonal-limit-compatibility-root-formal-seal-factorization}.
The diagonal seal-facing route has no source outside its displayed finite
tuple, so restricting it along the shared StreamName--RegSeqRat--DyadicRatCore--Real
rows gives precisely the CauchyCriterion selector-seal route. The excluded
objects have no coordinate in either accepted packet.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_selector\_seal\_route\_pullback}

\begin{theorem}[CauchyCriterion selector-seal synchronizer totality]
\label{thm:cauchycriterion-selector-seal-synchronizer-totality}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet. Suppose the two packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite-window selector rows at the completion-facing boundary. Then there is a total synchronizer route between the CauchyCriterion budget-selector surface and the UniformCauchyCriterion shared-threshold surface before any $\RealUp$ seal is consumed.

The synchronizer route is the common StreamName--RegSeqRat--DyadicRatCore--Real finite packet with its selector rows, $\BHist$ support, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and $\NameCert$ rows. It exposes no quotient stream, selected limit, host real equality, detached threshold family, ambient completeness principle, or second completion seal.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. It places every CauchyCriterion selector-facing read on the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ route before exposing selector output.

Apply \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility}. The CauchyCriterion selector route and the UniformCauchyCriterion shared-threshold seal route factor through the same finite packet before a $\RealUp$ seal is exposed.

Use the StreamName finite-window request and coverage rows together with the shared Real-facing handoff. They make the selector rows total over the displayed finite windows rather than over an ambient completion object.

Finally read the UniformCauchyCriterion shared-threshold transport and non-escape boundary. The uniform route contributes no detached threshold family or second seal, so the common packet gives the total synchronizer route claimed above.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_selector\_seal\_synchronizer\_totality}

\begin{theorem}[CauchyCriterion common selector refinement]
\label{thm:cauchycriterion-common-selector-refinement}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows at the completion-facing boundary. Then the Cauchy selector route, the uniform shared-threshold route, and the diagonal root-formal route determine one common finite selector-refinement packet over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The refinement packet exposes no quotient stream, selected host limit, host real equality, detached threshold family, ambient completeness principle, or second completion seal.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_common\_selector\_refinement}
\begin{proof}
First assemble the pairwise selector boundary. The uniform selector-seal compatibility theorem, \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility}, identifies the CauchyCriterion selector route and the UniformCauchyCriterion shared-threshold route inside one finite packet over the shared StreamName--RegSeqRat--DyadicRatCore--Real rows.

Next pull the diagonal route back to the same boundary. The route-pullback theorem, \autoref{thm:cauchycriterion-selector-seal-route-pullback}, restricts the diagonal root-formal seal route along the displayed finite rows and prevents it from exposing a detached completion object.

Finally apply synchronizer totality, \autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}. Its synchronizer packet already carries the finite selector rows, $\BHist$ support, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and $\NameCert$ rows. The StreamName finite-window and diagonal root-formal references used above put all three routes on that same finite window, so repacking them gives the common selector-refinement packet and no excluded coordinate remains.
\end{proof}

\begin{theorem}[CauchyCriterion TailCofinalitySchedule selector cofinality]
\label{thm:cauchycriterion-tailcofinalityschedule-selector-cofinality}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and let
$S=(E_S,W_S,D_S,R_S,L_S,H_S,C_S,P_S,N_S)$ be an accepted
$\TailCofinalityScheduleUp$ packet. Suppose the two packets share the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, finite-window
selector rows, componentwise $\hsame$ transport, displayed $\Cont$ routes,
$\Pkg$ provenance, and local $\NameCert$ rows. Then the accepted packets
determine one cofinal finite selector route through the Cauchy rows
$M,Q,T,W,E,H,C,P,N$ and the schedule rows $E_S,W_S,D_S,R_S,L_S,H_S,C_S,P_S,N_S$
before any $\RealUp$ or completion seal is public.

The route is the common StreamName--RegSeqRat--DyadicRatCore--Real finite packet
with its selector request, finite StreamName window, dyadic threshold ledger,
regular-rational readback, Real seal boundary, and structural support rows. It
exports no quotient stream, selected host limit, host real equality,
countable-choice schedule, ambient completeness principle, hidden tail oracle,
or second selector-budget source.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_tailcofinalityschedule\_selector\_cofinality}
\begin{proof}
First read the Cauchy side through
\autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. This
places every selector-facing $\CauchyCriterionUp$ read on the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows before a
selector output or Real seal can be inspected.

Next apply \autoref{thm:cauchycriterion-common-selector-refinement}. The Cauchy
selector route is already repacked with the uniform and diagonal routes over
the same finite rows, with support carried by $\BHist$, componentwise $\hsame$,
displayed $\Cont$, $\Pkg$, and $\NameCert$.

Now pass through the sibling schedule. The shared-tail budget factorization
theorem, \autoref{thm:tail-cofinality-schedule-shared-tail-budget-factorization},
places the schedule packet on the finite route through $E_S,W_S,D_S,R_S,L_S$
and the structural rows $H_S,C_S,P_S,N_S$, with no second tail-budget source.

Finally use
\autoref{thm:tail-cofinality-schedule-real-completion-diagonal-route}. It puts
the completion-facing diagonal read on the same schedule route before any public
$\RealUp$ or completion seal is available. Since both sides consume the
displayed StreamName--RegSeqRat--DyadicRatCore--Real rows with the same support
inventory, the Cauchy selector packet and the tail cofinality schedule determine
one cofinal finite route, and the excluded quotient, selected-limit,
host-equality, choice, completeness, hidden-oracle, and second-budget
coordinates have no carrier slot on that route.
\end{proof}

\begin{theorem}[CauchyCriterion Real-window diagonal selector lock]
\label{thm:cauchycriterion-real-window-diagonal-selector-lock}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows at the completion-facing boundary. Then every $\RealUp$ window selector read factors through one common finite packet over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The common packet contains no quotient stream, selected host limit, host real equality, detached threshold family, ambient completeness principle, or second seal.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_real\_window\_diagonal\_selector\_lock}
\begin{proof}
First read the CauchyCriterion selector boundary through \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. This places every Real-facing budget-selector read on the displayed StreamName--RegSeqRat--DyadicRatCore--Real rows before any external limit or completion coordinate can be inspected.

Next apply uniform selector-seal compatibility and route pullback, \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility} and \autoref{thm:cauchycriterion-selector-seal-route-pullback}. The uniform shared-threshold route and the diagonal root-formal route are both restricted to the same finite selector surface.

Now use synchronizer totality, \autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}. It supplies the total route that aligns the CauchyCriterion selector surface with the UniformCauchyCriterion shared-threshold surface over the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Finally invoke the common selector refinement theorem, \autoref{thm:cauchycriterion-common-selector-refinement}. Carrier-coordinate exhaustion leaves exactly the shared finite packet and removes every coordinate listed outside it, so each Real-window selector read is locked to that packet.
\end{proof}

\begin{theorem}[CauchyCriterion four-face selector readback determinacy]
\label{thm:cauchycriterion-four-face-selector-readback-determinacy}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows at the completion-facing boundary. Then any two $\RealUp$ or $\CompletionUp$ consumer readbacks preserving the common selector-refinement packet of \autoref{thm:cauchycriterion-common-selector-refinement} and the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows determine the same finite selector-readback packet before any seal is read.

The determinacy claim does not identify quotient streams, selected host limits, host real values, countable-choice selectors, ambient completeness witnesses, or a second seal source.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_four\_face\_selector\_readback\_determinacy}
\begin{proof}
First build the four-face boundary. Apply \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary} to place every CauchyCriterion selector-facing read on the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows, and use \autoref{thm:cauchycriterion-finite-request-section-return} to return the finite selector section without leaving those rows.

Next synchronize the two external routes. The uniform compatibility theorem, \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility}, puts the shared-threshold route on the same selector surface, while the pullback theorem, \autoref{thm:cauchycriterion-selector-seal-route-pullback}, restricts the diagonal root-formal route to that surface before a completion seal is exposed.

Now apply synchronizer totality, \autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}, and then the common refinement theorem, \autoref{thm:cauchycriterion-common-selector-refinement}. Together they package the common finite selector rows with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Finally use terminal non-escape, \autoref{thm:cauchycriterion-selector-refinement-terminal-nonescape}. Since both consumer readbacks preserve the same refinement packet and the same support rows, neither can add an extra selector coordinate after the common packet is fixed. The excluded quotient stream, selected host limit, host real equality, countable-choice selector, ambient completeness witness, and second seal source therefore have no coordinate along which the two readbacks could diverge.
\end{proof}

\begin{theorem}[CauchyCriterion selector-refinement terminal non-escape]
\label{thm:cauchycriterion-selector-refinement-terminal-nonescape}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows at the completion-facing boundary. Once the common selector-refinement packet of \autoref{thm:cauchycriterion-common-selector-refinement} is assembled, every terminal $\RealUp$ or $\CompletionUp$ consumer factors through that packet.

Consequently no terminal consumer exports quotient streams, selected host limits, host real equality, detached threshold families, ambient completeness, or a second completion seal.
\end{theorem}
\begin{proof}
First use \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}. It places the CauchyCriterion terminal read behind the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ selector boundary.

Next combine \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility} with \autoref{thm:cauchycriterion-selector-seal-route-pullback}. The uniform shared-threshold route and the diagonal root-formal route both restrict to the same selector-seal surface, with support carried by $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Now apply \autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}. The synchronizer is total on the finite selector rows, so any $\RealUp$ or $\CompletionUp$ consumer reaching the boundary has a route through the common packet.

Finally read the assembled packet through \autoref{thm:cauchycriterion-common-selector-refinement}. Since that theorem has already removed quotient streams, selected host limits, host real equality, detached threshold families, ambient completeness, and second completion seals from the shared packet, the same exclusions hold for terminal consumers.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_selector\_refinement\_terminal\_nonescape}

\begin{theorem}[CauchyCriterion diagonal selector terminality]
\label{thm:cauchycriterion-diagonal-selector-terminality}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let $U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted $\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows at the completion-facing boundary. Then the common selector-refinement packet of \autoref{thm:cauchycriterion-common-selector-refinement} is terminal among all $\RealUp$ or $\CompletionUp$ consumers preserving those displayed rows.

Equivalently, every such consumer factors through the same selector-refinement packet before any terminal seal is read, and no consumer preserving the displayed rows can add quotient streams, selected host limits, host real equality, countable-choice selectors, ambient completeness, or a second seal source.
\end{theorem}
\begin{proof}
First assemble the shared packet by \autoref{thm:cauchycriterion-common-selector-refinement}. That theorem composes the CauchyCriterion selector route, the UniformCauchyCriterion shared-threshold route, and the DiagonalLimitCompatibility route over the common $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and finite selector rows.

Next use the budget-selector boundary \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}, the route pullback \autoref{thm:cauchycriterion-selector-seal-route-pullback}, and synchronizer totality \autoref{thm:cauchycriterion-selector-seal-synchronizer-totality}. These rows place every Real or completion-facing read that preserves the displayed rows inside the same finite selector surface.

Finally apply terminal non-escape, \autoref{thm:cauchycriterion-selector-refinement-terminal-nonescape}. Since every terminal consumer already factors through the common packet, the packet is terminal among consumers preserving the shared rows. The excluded quotient stream, selected host limit, host real equality, countable-choice selector, ambient completeness, and second seal source coordinates are absent from the assembled packet and cannot be supplied by a terminal consumer.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_diagonal\_selector\_terminality}

\begin{theorem}[CauchyCriterion finite selector exhaustion]
\label{thm:cauchycriterion-finite-selector-exhaustion}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$U=(I,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted
$\UniformCauchyCriterionUp$ packet, and let $D$ be an accepted
$\DiagonalLimitCompatibilityUp$ packet. Suppose the three packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and
finite selector rows at the completion-facing boundary. Then every $\RealUp$
or $\CompletionUp$ consumer preserving those displayed rows factors through
exactly the finite selector-refinement packet of
\autoref{thm:cauchycriterion-common-selector-refinement}.

Conversely, any route through that selector-refinement packet supplies all
selector data available to such consumers: the common finite selector rows,
the $\BHist$ support, the componentwise $\hsame$ transports, the displayed
$\Cont$ routes, the $\Pkg$ provenance, and the $\NameCert$ rows. No quotient
stream, selected host limit, host real equality, countable-choice selector,
ambient completeness witness, detached threshold family, or second seal source
is available to a consumer preserving only the displayed rows.
\end{theorem}
\begin{proof}
First apply the boundary and return rows. The budget-selector boundary
\autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary} places
every selector-facing read on the displayed StreamName--RegSeqRat--DyadicRatCore--Real
surface, and the finite-request section return
\autoref{thm:cauchycriterion-finite-request-section-return} identifies the
finite selector section before any $\RealUp$ seal is exposed.

Next align the seal-facing routes. The uniform compatibility theorem
\autoref{thm:cauchycriterion-uniform-selector-seal-compatibility} and the
pullback theorem \autoref{thm:cauchycriterion-selector-seal-route-pullback}
put the CauchyCriterion, UniformCauchyCriterion, and DiagonalLimitCompatibility
routes on the same finite structural rows carried by $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$.

Now use synchronizer totality and common refinement. The synchronizer theorem
\autoref{thm:cauchycriterion-selector-seal-synchronizer-totality} makes the
finite selector surface total for the shared packets, while
\autoref{thm:cauchycriterion-common-selector-refinement} repacks that surface
as one selector-refinement packet over exactly the displayed support rows.

Finally apply diagonal selector terminality,
\autoref{thm:cauchycriterion-diagonal-selector-terminality}. Any $\RealUp$ or
$\CompletionUp$ consumer preserving the displayed rows must factor through the
same refinement packet. Inspecting the packet coordinates gives the converse:
a route through the packet provides precisely the selector rows and support
rows listed in the statement, and every omitted object has no coordinate from
which such a consumer could read it.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_finite\_selector\_exhaustion}

\begin{theorem}[CauchyCriterion finite-observation budget selector pullback]
\label{thm:cauchycriterion-finite-observation-budget-selector-pullback}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and
let $F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet. Suppose the two packets share the
displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$
rows at the selector-to-seal boundary, and suppose their $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ support rows are compatible componentwise. Then the
CauchyCriterion selector route and the finite observation-budget selector
route determine the same finite pullback surface from selector request to
$\RealUp$ seal.

The pullback surface contains exactly the displayed selector request, finite
StreamName window, dyadic readback, RegSeqRat handoff, Real seal, transport,
continuation, package, and local naming rows. It refuses quotient streams,
selected host limits, host real equality, countable choice, hidden selectors,
ambient completeness, and any second completion seal.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_finite\_observation\_budget\_selector\_pullback}
\begin{proof}
First place the CauchyCriterion side on the selector boundary. Apply
\autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary} and
\autoref{thm:cauchycriterion-selector-seal-route-pullback}; these identify the
displayed StreamName, DyadicRatCore, RegSeqRat, and Real rows used before the
seal is read.

Next make the CauchyCriterion selector total on that surface. Use
\autoref{thm:cauchycriterion-selector-seal-synchronizer-totality} and
\autoref{thm:cauchycriterion-finite-selector-exhaustion} to show that every
consumer preserving the displayed rows factors through the same finite
selector-refinement packet.

Now read the finite observation-budget selector packet. The obligations of
\autoref{thm:finite-observation-budget-selector-namecert-obligations} expose
the same kind of finite budget, window, dyadic, handoff, seal, transport,
continuation, package, and local naming rows. Route determinacy,
\autoref{thm:finite-observation-budget-selector-budget-route-determinacy},
forces the selector request to reach the Real seal along that displayed chain.

Finally apply the diagonal consumer boundary,
\autoref{thm:finite-observation-budget-selector-diagonal-consumer-boundary}.
Because both accepted packets preserve the same support rows, the two chains
meet in one finite pullback surface. The excluded quotient stream, selected
host limit, host real equality, countable-choice, hidden-selector, ambient
completeness, and second-seal objects have no coordinate in either packet, so
they cannot appear in the pullback.
\end{proof}

\begin{theorem}[CauchyCriterion finite-observation budget selector uniqueness]
\label{thm:cauchycriterion-finite-observation-budget-selector-uniqueness}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, and
let $F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ and
$F'=(B',S',V',D',R',E_{F'},H_{F'},C_{F'},P_{F'},N_{F'})$ be accepted
$\FiniteObservationBudgetSelectorUp$ packets. Suppose both $F$ and $F'$ share
the same packet $K$, the same displayed $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, and $\RealUp$ rows at the selector-to-seal boundary, and
componentwise compatible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support
rows. Then the two selector-to-seal pullback surfaces are the same finite BEDC
packet before any $\RealUp$ seal is read.

Equivalently, the shared surface is determined by the selector request, finite
StreamName window, dyadic readback, RegSeqRat handoff, pre-seal Real row,
transport, continuation, package, and local naming rows. It carries no
quotient streams, selected host limits, host real equality, countable choice,
hidden selectors, ambient completeness, or second completion seals.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_finite\_observation\_budget\_selector\_uniqueness}
\begin{proof}
First apply the pullback theorem
\autoref{thm:cauchycriterion-finite-observation-budget-selector-pullback} to
the pair $(K,F)$ and again to the pair $(K,F')$. Both applications land on a
finite selector-to-seal surface with exactly the displayed StreamName,
DyadicRatCore, RegSeqRat, Real, transport, continuation, package, and naming
rows.

Next use finite selector exhaustion,
\autoref{thm:cauchycriterion-finite-selector-exhaustion}. Because both
observation-budget packets preserve the same CauchyCriterion packet and the
same displayed rows, every completion-facing consumer factors through the
same selector-refinement packet before any Real seal is exposed.

It remains to identify the observation-budget routes into that packet. Route
determinacy,
\autoref{thm:finite-observation-budget-selector-budget-route-determinacy},
forces each accepted selector request to reach the Real row along the displayed
finite chain, and the diagonal consumer boundary,
\autoref{thm:finite-observation-budget-selector-diagonal-consumer-boundary},
keeps terminal consumers on that same chain.

Thus the two accepted packets have no remaining coordinate on which their
pullback surfaces can differ. Since quotient streams, selected host limits,
host real equality, countable choice, hidden selectors, ambient completeness,
and second completion seals are excluded from the shared packet, they cannot
serve as witnesses of a second selector-to-seal surface.
\end{proof}

\begin{theorem}[CauchyCriterion exact-boundary selector handoff]
\label{thm:cauchycriterion-exact-boundary-selector-handoff}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet, and let
$X=(L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X)$ be an accepted
$\RealCompletionExactBoundaryUp$ packet. Suppose the three packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$,
componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows
at the selector-to-seal boundary. Then the CauchyCriterion selector-to-seal
surface factors through the exact-boundary packet $X$ before any terminal
$\RealUp$ seal is read.

The handoff exposes only the selector request, finite StreamName window,
RegSeqRat handoff, DyadicRatCore tolerance row, terminal Real boundary, and
the shared $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. It refuses
quotient streams, selected host limits, host real equality, countable choice,
ambient completeness, and any second seal source.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_exact\_boundary\_selector\_handoff}
\begin{proof}
First apply
\autoref{thm:cauchycriterion-finite-observation-budget-selector-pullback}.
The accepted CauchyCriterion packet and the accepted finite observation-budget
selector packet meet on a single selector-to-seal pullback surface with the
displayed StreamName, RegSeqRat, DyadicRatCore, Real, transport,
continuation, package, and local naming rows.

Next use \autoref{thm:cauchycriterion-finite-selector-exhaustion}. It shows
that every completion-facing consumer preserving those rows must pass through
the same finite selector-refinement packet before a Real or Completion seal is
read.

Now apply
\autoref{thm:real-completion-exact-boundary-four-face-exactness}. The accepted
exact-boundary packet exports exactly the StreamName, RegSeqRat,
DyadicRatCore, and terminal Real faces on the route
$L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X$, so the selector-refinement
surface has only that exact-boundary consumer route available.

Finally use
\autoref{thm:real-completion-exact-boundary-real-seal-nonescape}. The terminal
Real seal cannot be read outside the exact-boundary packet. Since the pullback
and exhaustion steps already removed quotient streams, selected host limits,
host real equality, countable choice, ambient completeness, hidden selectors,
and second seal sources, the selector-to-seal surface factors through the
exact-boundary packet before any terminal Real seal is consumed.
\end{proof}

\begin{theorem}[CauchyCriterion StreamName--Real budget selector terminal boundary]
\label{thm:cauchy-criterion-streamname-real-budget-selector-terminal-boundary}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet, and let
$X=(L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X)$ be an accepted
$\RealCompletionExactBoundaryUp$ packet. Suppose the packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$,
componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.
Then every terminal $\RealUp$ or $\CompletionUp$ selector read of the shared
surface factors through the exact-boundary selector handoff of
\autoref{thm:cauchycriterion-exact-boundary-selector-handoff}.

Conversely, that handoff supplies all selector data available to such a
terminal read: the selector request, finite StreamName window, RegSeqRat
handoff, DyadicRatCore tolerance row, terminal Real boundary, and the displayed
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. It supplies no quotient
stream, selected host limit, host real equality, countable choice, ambient
completeness, hidden selector, or second seal source.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:cauchycriterion-finite-observation-budget-selector-pullback}. The
CauchyCriterion packet and the finite observation-budget selector packet meet
on the displayed finite selector-to-seal surface.

Next use
\autoref{thm:cauchycriterion-finite-observation-budget-selector-uniqueness}.
The finite surface is determined by the shared StreamName, RegSeqRat,
DyadicRatCore, Real, transport, continuation, package, and local naming rows,
so no second selector surface remains for a terminal read.

Now apply \autoref{thm:cauchycriterion-exact-boundary-selector-handoff}. It
routes the shared selector surface through the accepted exact-boundary packet
before a terminal Real or Completion selector read can consume the seal rows.

The exact-boundary inventory is fixed by
\autoref{thm:real-completion-exact-boundary-four-face-exactness}. Finally use
\autoref{thm:real-completion-exact-boundary-real-seal-nonescape} to block any
terminal seal escape. Thus the handoff gives exactly the selector data
available to the read, and all excluded host, quotient, choice, completeness,
hidden-selector, and second-seal coordinates remain outside the packet.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_streamname\_real\_budget\_selector\_terminal\_boundary}

\begin{theorem}[CauchyCriterion selector-budget three-way terminality]
\label{thm:cauchycriterion-selector-budget-three-way-terminality}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet, and let
$X=(L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X)$ be an accepted
$\RealCompletionExactBoundaryUp$ packet. Suppose the three packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$,
componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.
Then the finite-request section, the finite observation-budget selector, and
the exact-boundary handoff determine one terminal selector-to-seal packet before
any terminal $\RealUp$ or $\CompletionUp$ read.

That terminal packet contains exactly the displayed selector request, finite
StreamName window, RegSeqRat handoff, DyadicRatCore tolerance row, terminal Real
boundary, and the shared $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support. It
contains no quotient stream, selected host limit, host real equality, countable
choice, ambient completeness, hidden selector, or second seal source.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchycriterion-finite-request-section-return}. The
accepted CauchyCriterion packet returns its finite request section on the
displayed StreamName, RegSeqRat, DyadicRatCore, Real, transport, continuation,
package, and local naming rows.

Next apply \autoref{thm:cauchycriterion-common-selector-refinement}. This
places the finite request section on the common selector-refinement packet
shared by the CauchyCriterion route and the completion-facing rows.

Now use
\autoref{thm:cauchycriterion-finite-observation-budget-selector-uniqueness}. It
shows that the accepted finite observation-budget selector has no second packet
with the same displayed rows, so the selector component of the terminal surface
is unique.

Finally apply
\autoref{thm:cauchy-criterion-streamname-real-budget-selector-terminal-boundary}.
The exact-boundary handoff is the only terminal selector-to-seal packet available
before a $\RealUp$ or $\CompletionUp$ read. Its inventory already excludes
quotient streams, selected host limits, host real equality, countable choice,
ambient completeness, hidden selectors, and second seal sources, so the three
presentations determine the same terminal packet.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_selector\_budget\_three\_way\_terminality}

\begin{theorem}[CauchyCriterion terminal selector-seal no-choice exhaustion]
\label{thm:cauchycriterion-terminal-selector-seal-nochoice-exhaustion}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet, and let
$X=(L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X)$ be an accepted
$\RealCompletionExactBoundaryUp$ packet. Suppose the three packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$,
componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.
Then every terminal selector-to-seal read of the shared surface factors through,
in order, the finite-request section, the finite observation-budget selector,
the exact-boundary handoff, and the three-way terminal packet of
\autoref{thm:cauchycriterion-selector-budget-three-way-terminality}.

The resulting consumer-visible boundary exports only the selector request,
finite StreamName window, RegSeqRat handoff, DyadicRatCore tolerance row,
terminal Real boundary, and the shared $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ support rows. It exports no quotient stream, selected host limit,
host real equality, countable-choice schedule, ambient completeness, hidden
selector, or second seal source.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchycriterion-finite-request-section-return}. The
accepted CauchyCriterion packet returns the finite request section on the shared
StreamName, RegSeqRat, DyadicRatCore, Real, transport, continuation, package,
and local naming rows.

Next use
\autoref{thm:cauchycriterion-finite-observation-budget-selector-uniqueness}.
This pins the finite observation-budget selector to the same displayed rows and
removes any second selector packet before a terminal read can consume the seal
surface.

Now apply \autoref{thm:cauchycriterion-exact-boundary-selector-handoff}. The
finite selector route is handed to the accepted exact-boundary packet, so every
terminal selector-to-seal read must pass through the displayed
$\RealCompletionExactBoundaryUp$ rows before a $\RealUp$ or $\CompletionUp$ seal
is read.

Finally combine
\autoref{thm:cauchy-criterion-streamname-real-budget-selector-terminal-boundary}
with \autoref{thm:cauchycriterion-selector-budget-three-way-terminality}. The
first theorem gives the terminal StreamName--Real boundary, while the second
identifies the finite-request, finite-budget, and exact-boundary presentations
as one terminal packet.

The carrier inventory of that packet is already exhausted by the displayed
selector request, finite StreamName window, RegSeqRat handoff, DyadicRatCore
tolerance row, terminal Real boundary, and shared support rows. Therefore a
terminal read has no exported quotient stream, selected host limit, host real
equality, countable-choice schedule, ambient completeness, hidden selector, or
second seal source available outside the stated route.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_terminal\_selector\_seal\_nochoice\_exhaustion}

\begin{theorem}[CauchyCriterion budget-selector section exactness]
\label{thm:cauchycriterion-budget-selector-section-exactness}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ packet, let
$F=(B,S,V,D,R,E_F,H_F,C_F,P_F,N_F)$ be an accepted
$\FiniteObservationBudgetSelectorUp$ packet, and let
$X=(L,K_X,J_X,S_X,W_X,R_X,D_X,E_X,H_X,C_X,P_X,N_X)$ be an accepted
$\RealCompletionExactBoundaryUp$ packet. Suppose the three packets share the
displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$,
componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows
over the same $\BHist$ support. Then every finite observation request routed
through the displayed $\StreamNameUp$--$\RegSeqRat$--$\RealUp$ selector surface
has a unique budget-selector section.

Replaying that section through the selector-seal route returns the same finite
StreamName window, RegSeqRat handoff, DyadicRatCore tolerance row, terminal
$\RealUp$ boundary, and seal row carried by the original request. No quotient
stream, host real equality, selected-limit oracle, countable-choice row,
ambient completeness witness, hidden selector, or second seal source is
introduced.
\end{theorem}
\begin{proof}
First apply \autoref{thm:cauchycriterion-finite-request-section-return}. It
returns the finite request section on the displayed StreamName, RegSeqRat,
DyadicRatCore, Real, transport, continuation, package, and local naming rows
over the given $\BHist$ support.

Next use
\autoref{thm:cauchycriterion-finite-observation-budget-selector-pullback}. The
accepted finite observation-budget selector and the accepted CauchyCriterion
packet meet on the same selector-to-seal pullback surface, so the returned
section is already routed through the displayed $\StreamNameUp$--$\RegSeqRat$--$\RealUp$
surface.

Now apply
\autoref{thm:cauchycriterion-finite-observation-budget-selector-uniqueness}.
This proves that no second accepted budget-selector section with the same
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows can determine a
different finite window or seal-facing row.

Finally combine
\autoref{thm:cauchycriterion-selector-seal-synchronizer-totality} with
\autoref{thm:cauchycriterion-terminal-selector-seal-nochoice-exhaustion}. The
synchronizer makes replay through the selector-seal route total on the finite
surface, and no-choice exhaustion says the replay has no exported coordinate
for a quotient stream, host real equality, selected-limit oracle,
countable-choice row, ambient completeness witness, hidden selector, or second
seal source. Therefore replay returns exactly the original finite window and
seal row.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_budget\_selector\_section\_exactness}

\begin{theorem}[CauchyCriterion budget-selector terminal route exhaustion]
\label{thm:cauchycriterion-budget-selector-terminal-route-exhaustion}
Let $K=(W,M,T,Q,E,H,C,P,N)$ be an accepted $\CauchyCriterionUp$ budget-selector route over the displayed $\BHist$ support. Among routes that share the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, finite selector, uniform threshold, and diagonal root-formal surfaces, the accepted route is terminal. Every such route factors through the finite rows already named by the boundary theorem, finite-request section return, uniform compatibility, diagonal pullback, common selector refinement, finite selector exhaustion, terminality, and budget-selector section exactness in this chapter.

Consequently no accepted route over the same surfaces can add a quotient stream, host real equality, countable-choice selector, ambient completeness witness, detached threshold, or second seal. Any consumer that asks for one of those rows has left the $\CauchyCriterionUp$ budget-selector route rather than extending it.
\end{theorem}
\begin{proof}
First apply the boundary theorem and finite-request section return. These place the accepted route on the displayed StreamName, RegSeqRat, DyadicRatCore, Real, transport, continuation, package, and local naming rows.

Next use uniform compatibility and the diagonal pullback. They keep the uniform threshold and diagonal root-formal surfaces on the same finite support, so a route sharing those surfaces cannot detach its threshold or introduce a second root source.

Now apply common selector refinement and finite selector exhaustion. The selector row is already fixed by the shared finite request and by the accepted finite observation-budget selector, leaving no second selector packet with the same displayed rows.

Finally combine terminality with \autoref{thm:cauchycriterion-budget-selector-section-exactness}. The section exactness theorem returns the same finite window and seal row under replay, while terminality blocks quotient streams, host real equality, countable-choice selectors, ambient completeness, detached thresholds, and second seals. Thus every shared-surface route factors through the named finite rows and no additional route coordinate remains.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_budget\_selector\_terminal\_route\_exhaustion}

\begin{theorem}[CauchyCriterion StreamName Real budget bridge readiness]
\label{thm:cauchycriterion-streamname-real-budget-bridge-readiness}
Every bridge-ready $\CauchyCriterionUp$ selector route factors through the displayed $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, finite-observation budget selector, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:cauchycriterion-budget-selector-terminal-route-exhaustion}. It makes the accepted selector route terminal over the named finite surfaces.

Then read the boundary, section-return, and exactness theorems already cited there. They keep bridge readiness on $W,M,T,Q,E,H,C,P,N$ and add no quotient stream, hidden selector, countable-choice row, or ambient Real-completeness premise.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCriterionUp.CauchyCriterionCarrier\_streamname\_real\_budget\_bridge\_readiness}

\begin{theorem}[CauchyCriterion selector budget formal target boundary]
\label{thm:cauchycriterion-selector-budget-formal-target-boundary}
A later formal target for the $\CauchyCriterionUp$ StreamName-to-Real budget selector may consume only the finite selector-budget boundary named in \autoref{thm:cauchycriterion-streamname-real-budget-bridge-readiness}. It may not import quotient stream equality, countable choice, ambient Real completeness, or a hidden selector.
\end{theorem}
\begin{proof}
Use bridge readiness to enumerate the admissible inputs. The formal target receives the StreamName window, RegSeqRat readback, DyadicRatCore ledger, RealUp seal, finite selector, transport, replay, provenance, and naming rows.

Now apply terminal route exhaustion. Any additional quotient equality, choice selector, completeness witness, or hidden selector would be a new coordinate outside the terminal finite route, so it is not part of the formal boundary.
\end{proof}
