\subsection{Channel encoding and genetic-code bridge}
\label{subsec:philosophy-channel-genetic-code-bridge}

The relation between the BEDC channel compiler and biological genetic
coding is structural rather than token-identical. The BEDC channel code
is a minimal self-delimiting event-stream codec. The DNA and RNA genetic
codes are fixed-frame biological translation codecs over finite
alphabets. Both systems combine a finite alphabet, a local reading
discipline, a boundary or stop class, and an interpretation layer, but
the corresponding objects live at different layers.

This subsection is a vision-level scientific-model bridge. It is not a
CheckedCert claim about molecular biology, and it does not turn a
channel glyph into a biological base, codon, or biochemical law. Its
governing discipline is the decode-first principle of
\autoref{prin:analysis-pipeline-decode-first}: channel strings may be
analyzed only after they have been decoded to source event flows.

\begin{definition}[Active channel event]
\label{def:philosophy-active-channel-event}
Let $\Sigma=\{0,1\}$. A raw event is a finite word in $\Sigma^{*}$, and
an event flow is a finite sequence of raw events. The active BEDC
channel layer uses the Zeckendorf-safe body substitution
$$
\begin{aligned}
  \zeta(\epsilon) &= \epsilon,\\
  \zeta(0w) &= 0\,\zeta(w),\\
  \zeta(1w) &= 10\,\zeta(w),
\end{aligned}
$$
with event terminator $11$. The channel event associated to a raw event
$w$ is
$$
  \mathsf{Ev}(w)=\zeta(w)\,11.
$$
\end{definition}

\begin{definition}[Legal channel stream]
\label{def:philosophy-legal-channel-stream}
A legal BEDC channel stream is a finite concatenation of channel
events:
$$
  \mathsf{LegalZStream}
  =
  \big((0\mid 10)^{*}\,11\big)^{*}.
$$
Equivalently, the active local channel rules are
$$
\begin{aligned}
  \mathrm{raw}\ 0 &\longmapsto 0,\\
  \mathrm{raw}\ 1 &\longmapsto 10,\\
  \mathrm{End} &\longmapsto 11.
\end{aligned}
$$
\end{definition}

\begin{theorem}[The active channel body has no terminator]
\label{thm:philosophy-channel-body-no-terminator}
For every raw event $w$, the encoded body $\zeta(w)$ contains no
adjacent substring $11$.
\end{theorem}
\begin{proof}
The body is a finite concatenation of fragments from $\{0,10\}$. Neither
fragment contains $11$. The only possible fragment junctions are
$00$, $010$, $100$, and $1010$, and none of these contains $11$. Hence
no adjacent $11$ occurs before the appended terminator.
\end{proof}

\begin{corollary}[The first $11$ is the channel terminator]
\label{cor:philosophy-first-11-channel-terminator}
For every raw event $w$, the first adjacent occurrence of $11$ in
$\mathsf{Ev}(w)=\zeta(w)\,11$ is the appended event terminator.
\end{corollary}
\begin{proof}
By \autoref{thm:philosophy-channel-body-no-terminator}, the encoded body
has no adjacent $11$. The only remaining adjacent $11$ is the appended
terminator.
\end{proof}

\begin{theorem}[Channel round trip]
\label{thm:philosophy-channel-round-trip}
For every event flow $S$, decoding the compiled channel stream recovers
the original source event flow:
$$
  \mathsf{Decode}(\mathsf{Compile}(S))=\mathsf{some}(S).
$$
On legal channel streams, $\mathsf{Compile}$ and $\mathsf{Decode}$ form
an inverse pair between $\mathsf{EventFlow}$ and
$\mathsf{LegalZStream}$.
\end{theorem}
\begin{proof}
Each encoded event has a unique first $11$ terminator by
\autoref{cor:philosophy-first-11-channel-terminator}. The stream decoder
therefore segments a compiled string exactly at event boundaries, then
decodes each body by the inverse local readings $0\mapsto\mathrm{raw}\ 0$
and $10\mapsto\mathrm{raw}\ 1$. This is the vision-level restatement of
the checked channel bijection recorded in
\autoref{cor:channel-encoding-bijection}.
\end{proof}

\begin{remark}[The rejected channel rule]
\label{rem:philosophy-rejected-channel-rule}
The displayed rule $\mathrm{raw}\ 1\mapsto 01$ is not the active BEDC
channel rule. If it were paired with the same terminator $11$, the event
$1$ would be displayed as $0111$. A streaming decoder would consume the
leading $0$ as body data, read $11$ as a terminator, and leave an
isolated malformed $1$. This is exactly the failure isolated by
\autoref{prop:channel-encoding-0111-illegal}. The active rule
$\mathrm{raw}\ 1\mapsto 10$ avoids the collision.
\end{remark}

\begin{theorem}[Layer separation for channel and source readings]
\label{thm:philosophy-channel-source-layer-separation}
The channel-level terminator $11$ cannot be reinterpreted as a
source-level raw substring, a source-level rewrite, a DNA base, a stop
codon, or a theorem judgment without an explicit bridge.
\end{theorem}
\begin{proof}
The source layer and the channel layer share displayed glyphs but not
typing judgments. In the source layer, $11$ may occur inside a raw
event. In the channel layer, $11$ marks the end of a channel-encoded
event. By \autoref{thm:source-channel-layer-separation}, a displayed
channel substring is not, in general, a decoded source event. A
biological or theorem-level reading therefore requires a separate
bridge after decoding.
\end{proof}

\begin{definition}[DNA four-phase alphabet bridge]
\label{def:philosophy-dna-four-phase-alphabet-bridge}
The canonical DNA alphabet is the four-base alphabet
$$
  \mathsf{DNA}_{4}:=\{\mathrm{A},\mathrm{C},\mathrm{G},\mathrm{T}\}.
$$
A DNA four-phase alphabet bridge is a conservative external readback
from the BEDC product of two Bool-like interfaces to this external
alphabet:
$$
  \beta_{\mathsf{DNA}}
  \colon
  \BoolUp\times\BoolUp
  \rightsquigarrow
  \mathsf{DNA}_{4}.
$$
One biologically meaningful readback uses one axis for purine versus
pyrimidine shape and the other for AT-family versus GC-family pairing.
\end{definition}
\concretizedIn{ch:concrete-instances-dna-four-phase-alphabet-bridge-namecert}{Realizes the four-phase DNA alphabet readback as a conservative finite NameCert bridge.}

\begin{definition}[Complementation readback]
\label{def:philosophy-dna-complementation-readback}
Under the shape-family readback, the four displayed phases are
$$
\begin{aligned}
  \mathrm{A} &= (\mathrm{purine},\mathrm{AT}),\\
  \mathrm{G} &= (\mathrm{purine},\mathrm{GC}),\\
  \mathrm{T} &= (\mathrm{pyrimidine},\mathrm{AT}),\\
  \mathrm{C} &= (\mathrm{pyrimidine},\mathrm{GC}).
\end{aligned}
$$
The biological complementation operation is then read as the partial
external involution
$$
  \mathrm{comp}(\mathrm{shape},\mathrm{family})
  =
  (\mathrm{flip}(\mathrm{shape}),\mathrm{family}),
$$
which displays $\mathrm{A}\leftrightarrow\mathrm{T}$ and
$\mathrm{G}\leftrightarrow\mathrm{C}$.
\end{definition}

\begin{theorem}[DNA four-base product bridge]
\label{thm:philosophy-dna-four-base-product-bridge}
The canonical DNA alphabet has a natural conservative readback as a
four-phase atlas over the product $\BoolUp\times\BoolUp$.
\end{theorem}
\begin{proof}
The interface $\BoolUp$ supplies a licensed two-endpoint BEDC finite
data surface, and $\ProdUp$ supplies the displayed product discipline
for componentwise finite data. The external biological bridge maps the
four displayed pairs to $\mathrm{A}$, $\mathrm{C}$, $\mathrm{G}$, and
$\mathrm{T}$. The bridge is conservative because the biological names
remain target-side readbacks; they do not become BEDC primitives.
\end{proof}

\begin{corollary}[Four as double distinction]
\label{cor:philosophy-dna-four-as-double-distinction}
Within this bridge, the displayed number $4$ is read as a product of
two binary distinctions rather than as a biological primitive:
$$
  4=2\times 2.
$$
\end{corollary}
\begin{proof}
Each coordinate of $\BoolUp\times\BoolUp$ is a binary classifier. The
product has four displayed phase positions, and the biological readback
assigns those positions to the four canonical bases.
\end{proof}

\begin{definition}[DNA four-phase bridge certificate template]
\label{def:philosophy-dna-four-phase-namecert-template}
At vision strength, the paper certificate template for the four-phase
DNA alphabet has the form
$$
\begin{aligned}
  \mathsf{NameCert}(\mathsf{DNA4Alphabet}^{\uparrow})
  =
  (&\mathsf{SourceSpec},
    \mathsf{PatternSpec},
    \mathsf{ClassifierSpec},\\
   &\mathsf{StabilityCert},
    \mathsf{LedgerPolicy}).
\end{aligned}
$$
The template records obligations for a conservative bridge target; it
is not a completed paper certificate and not a checked Lean target.
\end{definition}

\begin{definition}[DNA four-phase source and pattern fields]
\label{def:philosophy-dna-source-pattern-fields}
The source field consists of two previously licensed $\BoolUp$
interfaces combined through the $\ProdUp$ product interface, together
with the external biological target $\mathsf{DNA}_{4}$. The pattern
field consists of the four visible product phases
$$
\begin{gathered}
  (\mathrm{purine},\mathrm{AT}),
  \quad
  (\mathrm{pyrimidine},\mathrm{AT}),\\
  (\mathrm{purine},\mathrm{GC}),
  \quad
  (\mathrm{pyrimidine},\mathrm{GC}),
\end{gathered}
$$
and the complement involution
$$
  \mathrm{comp}(\mathrm{shape},\mathrm{family})
  =
  (\mathrm{flip}(\mathrm{shape}),\mathrm{family}).
$$
The source is the BEDC product carrier; the DNA alphabet is an external
readback target.
\end{definition}

\begin{definition}[DNA four-phase classifier, stability, and ledger fields]
\label{def:philosophy-dna-classifier-stability-ledger-fields}
The classifier field is the componentwise $\BoolUp$ classifier on the
product surface, together with external $\beta_{\mathsf{DNA}}$ readback
rows. The stability field requires product carrier closure under the
componentwise classifier, complement descent through the classifier,
the involution law for complement, absence of fixed points on the four
canonical rows, triple-product closure for the codon atlas, and
translation-classifier respect for codon classification at the external
bridge layer. The ledger policy is the displayed pair ledger for
$\mathsf{DNA4Alphabet}^{\uparrow}$, the displayed triple ledger for the
codon atlas, and the biological readback provenance
$\beta_{\mathsf{DNA}}$.
\end{definition}

\begin{theorem}[Complement is a fixed-point-free involution]
\label{thm:philosophy-dna-complement-involution}
For
$$
  \mathrm{comp}(\mathrm{shape},\mathrm{family})
  =
  (\mathrm{flip}(\mathrm{shape}),\mathrm{family}),
$$
the composite $\mathrm{comp}\circ\mathrm{comp}$ classifies with the
identity on the product phase level. On the four canonical DNA rows, the
complement map has no fixed point.
\end{theorem}
\begin{proof}
The first coordinate is flipped twice, so it returns to its original
classifier value, while the second coordinate is preserved. Since
$\mathrm{flip}$ has no fixed point on the two visible shape phases, the
product map has no fixed point on the four canonical rows.
\end{proof}

\begin{corollary}[Watson--Crick complement as product-axis flip]
\label{cor:philosophy-watson-crick-product-axis-flip}
Under $\beta_{\mathsf{DNA}}$, the complement map reads externally as
$$
  \mathrm{A}\leftrightarrow\mathrm{T},
  \qquad
  \mathrm{G}\leftrightarrow\mathrm{C}.
$$
\end{corollary}
\begin{proof}
$\mathrm{A}$ and $\mathrm{T}$ share the AT-family coordinate and differ
in shape; $\mathrm{G}$ and $\mathrm{C}$ share the GC-family coordinate
and differ in shape. Flipping shape while preserving family gives the
displayed pairings.
\end{proof}

\begin{definition}[Codon phase atlas]
\label{def:philosophy-codon-phase-atlas}
The codon phase atlas is the triple product of the DNA four-phase
alphabet:
$$
  \mathsf{Codon}_{64}^{\uparrow}
  :=
  (\mathsf{DNA}_{4}^{\uparrow})^{3}.
$$
Its external biological classifier separates amino-acid-emitting codons
from stop codons.
\end{definition}

\begin{corollary}[Codon phase-space bridge]
\label{cor:philosophy-codon-phase-space-bridge}
The codon layer has $64$ displayed phase positions.
\end{corollary}
\begin{proof}
The bridge target has four DNA phases, and a codon is a triple of such
phases. Therefore its displayed phase space has cardinality
$$
  4^{3}=64.
$$
The stop classifier is an external biological partition of this
phase-space. It is not the BEDC channel terminator.
\end{proof}

\begin{definition}[Genetic translation classifier]
\label{def:philosophy-genetic-translation-classifier}
A genetic translation classifier is an external biological classifier
of the form
$$
  \mathsf{TranslateClassifier}
  :
  \mathsf{Codon}_{64}^{\uparrow}
  \rightsquigarrow
  \mathsf{AminoAcid}^{\uparrow}\oplus\mathsf{Stop}^{\uparrow}.
$$
It may be many-to-one: distinct codon positions may classify to the
same amino-acid class. The original codon remains part of the ledger.
\end{definition}

\begin{definition}[Genetic-code ledger]
\label{def:philosophy-genetic-code-ledger}
A genetic-code ledger records the original codon triple, its three
$\mathsf{DNA4Alphabet}^{\uparrow}$ component positions, the
translation-classifier output, whether that output is amino-acid
emitting or stop, and the external biological bridge provenance used to
read each BEDC phase as a biological base.
\end{definition}

\begin{theorem}[Translation is a classifier quotient]
\label{thm:philosophy-translation-classifier-quotient}
Genetic translation, at this bridge strength, is represented by a
classifier from the codon atlas to amino-acid or stop classes, and that
classifier may be many-to-one.
\end{theorem}
\begin{proof}
A codon position is source-side phase material for the bridge. An
amino-acid or stop class is the classified visible output. Multiple
codon positions may classify to the same amino-acid class. BEDC reads
this as classifier quotient rather than as source erasure because
\autoref{def:philosophy-genetic-code-ledger} keeps the original codon
triple and component readbacks visible.
\end{proof}

\begin{corollary}[Synonymous codons are ledger-preserving compression]
\label{cor:philosophy-synonymous-codons-ledger-compression}
If two codons classify to the same amino-acid class, the visible
translation meaning is compressed while each original codon remains in
the ledger.
\end{corollary}
\begin{proof}
This is the biological bridge instance of BEDC compression with memory:
classification may hide distinctions at the visible meaning level, but
the source map remains recoverable through the ledger.
\end{proof}

\begin{corollary}[Codon length and alphabet size generate the phase space]
\label{cor:philosophy-codon-length-alphabet-size}
The codon layer combines binary distinction, double distinction, a
three-position reading window, and a stop classifier:
$$
\begin{gathered}
  2=\text{binary distinction},\\
  4=2\times 2=\text{DNA four-phase alphabet},\\
  4^{3}=64=\text{codon phase space}.
\end{gathered}
$$
\end{corollary}

\begin{definition}[Stop-role bridge]
\label{def:philosophy-stop-role-bridge}
The stop-role bridge relates two typed termination roles:
$$
\begin{aligned}
  \mathsf{ChannelEndRole}(11)
  &:\text{ event-boundary termination},\\
  \mathsf{GeneticStopRole}(\mathrm{codon})
  &:\text{ protein-translation termination}.
\end{aligned}
$$
The bridge asserts role analogy under finite-stream reading, not
identity of tokens.
\end{definition}

\begin{theorem}[Stop-role analogy is not token identity]
\label{thm:philosophy-stop-role-analogy-not-identity}
The BEDC channel terminator and biological stop codons have the same
abstract role of ending a finite reading process, but they are not the
same object.
\end{theorem}
\begin{proof}
The BEDC terminator $11$ ends one channel-encoded raw event inside
$\mathsf{LegalZStream}$. A biological stop codon ends protein synthesis
inside a codon reading frame. The former is a channel-boundary marker;
the latter is a translation-class marker in an external biological
model. Hence the licensed relation is role-equivalence under a
conservative bridge, not token identity.
\end{proof}

\begin{theorem}[Channel/genetic bridge cannot-claim boundary]
\label{thm:philosophy-channel-genetic-cannot-claim-boundary}
The channel/genetic-code bridge does not license any of the following
claims:
\begin{itemize}
  \item that BEDC channel encoding is DNA;
  \item that the channel glyph pair $11$ is a DNA or RNA stop codon;
  \item that $01$ is the active BEDC encoding of raw $1$;
  \item that a DNA base can be read directly from a compiled BEDC
    channel substring;
  \item that a biological bridge replaces BEDC NameCert obligations;
  \item that $\mathsf{DNA4Alphabet}^{\uparrow}$ is already a checked
    BEDC theorem;
  \item that the codon classifier is already a checked BEDC theorem.
\end{itemize}
\end{theorem}
\begin{proof}
The active channel rule for raw $1$ is $10$, not $01$, by
\autoref{def:philosophy-legal-channel-stream}. Channel substrings must
be decoded before source analysis by
\autoref{thm:philosophy-channel-source-layer-separation}. The DNA and
codon readings are external scientific-model bridges in the sense of
\autoref{def:philosophy-model-bridge}, and bridge targets do not replace
internal certificates by \autoref{cor:philosophy-host-maturity-not-replace-bedc-certification}.
The certificate fields in
\autoref{def:philosophy-dna-four-phase-namecert-template} are displayed
as a vision-strength template, so they do not by themselves supply a
checked theorem for either the DNA alphabet bridge or the translation
classifier.
\end{proof}

\begin{corollary}[Allowed bridge claim]
\label{cor:philosophy-channel-genetic-allowed-claim}
The allowed claim is that BEDC channel encoding supplies a minimal
self-delimiting event-stream skeleton, while DNA and RNA genetic coding
supply biological fixed-frame translation systems. Their formal
relation is a conservative finite-reading and stop-role bridge mediated
by decoding, the product surface $\BoolUp\times\BoolUp$, and the codon
phase atlas.
\end{corollary}

\begin{corollary}[Minimal channel skeleton and biological parser]
\label{cor:philosophy-minimal-channel-biological-parser}
The BEDC channel parser and the genetic-code parser share a finite
reading motif:
$$
\begin{gathered}
  0\longmapsto \mathrm{emit\ raw}\ 0,\qquad
  10\longmapsto \mathrm{emit\ raw}\ 1,\qquad
  11\longmapsto \mathrm{stop\ current\ event},\\
  \mathrm{codon}\longmapsto \mathrm{emit\ amino\ acid},\qquad
  \mathrm{stop\ codon}\longmapsto \mathrm{stop\ protein\ synthesis}.
\end{gathered}
$$
The shared structure is finite stream, local reading rule, stop class,
and ledger. The objects remain layer-distinct.
\end{corollary}
