\subsection{Codons as six-bit finite windows}
\label{subsec:philosophy-codon-window-six-bridge}

The four-phase DNA and RNA bridge of
\autoref{subsec:philosophy-channel-genetic-code-bridge} has a direct
finite-window reading. A codon is a three-position word over a
four-phase alphabet. Once each base is read through two binary axes, a
codon is exactly a six-bit window at the source-space level:
$$
  4^{3}=64=2^{6}.
$$
This is the strongest window-six contact point. It is a source-space
isomorphism, not an identification of the genetic-code translation
table with a BEDC fold table.

\begin{definition}[Codon six-bit source atlas]
\label{def:philosophy-codon-six-bit-source-atlas}
Let
$$
  \mathsf{RNA4Alphabet}^{\uparrow}
  :=
  \BoolUp\times\BoolUp
$$
be read externally by the two axes of
\autoref{def:philosophy-rna-two-axis-readback}. The codon source atlas
is
$$
  \mathsf{Codon64}^{\uparrow}
  :=
  (\mathsf{RNA4Alphabet}^{\uparrow})^{3}.
$$
The six-bit flattening map is the displayed reassociation
$$
  \mathsf{Flat}_{6}
  :
  (\BoolUp\times\BoolUp)^{3}
  \rightsquigarrow
  (\BoolUp)^{6},
$$
which reads a codon as three consecutive two-bit blocks.
\end{definition}

\begin{theorem}[Codon source space is a six-bit window]
\label{thm:philosophy-codon-source-space-six-bit-window}
At the source-space level, the codon atlas has the same finite carrier
size as the six-bit binary window:
$$
  \left|(\BoolUp\times\BoolUp)^{3}\right|
  =
  |(\BoolUp)^{6}|
  =
  64.
$$
\end{theorem}
\begin{proof}
Each $\BoolUp$ coordinate has two visible endpoints. Hence
$\BoolUp\times\BoolUp$ has $2\cdot 2=4$ visible phases, and a triple
of such phases has $4^{3}=64$ visible positions. Reassociation exposes
the same six binary coordinates, whose carrier size is $2^{6}=64$.
\end{proof}

\begin{definition}[RNA two-axis binary display]
\label{def:philosophy-rna-two-axis-binary-display}
Using the shape-family readback
$$
\begin{aligned}
  \mathrm{U} &= 00,&
  \mathrm{C} &= 01,\\
  \mathrm{A} &= 10,&
  \mathrm{G} &= 11,
\end{aligned}
$$
the four codons in the $\mathrm{U}+\mathrm{RR}$ square flatten as
$$
\begin{array}{c|c}
  \text{codon} & \mathsf{Flat}_{6}\text{ display}\\
\hline
  \mathrm{UAA} & 00\,10\,10\\
  \mathrm{UAG} & 00\,10\,11\\
  \mathrm{UGA} & 00\,11\,10\\
  \mathrm{UGG} & 00\,11\,11
\end{array}
$$
The DNA coding-strand display is obtained by replacing the first
$\mathrm{U}$ with $\mathrm{T}$; the six-bit source calculation is
unchanged.
\end{definition}

\begin{definition}[Window-six Zeckendorf target]
\label{def:philosophy-window-six-zeckendorf-target}
The window-six source space is
$$
  \Omega_{6}:=\{0,1\}^{6}.
$$
Its Zeckendorf-legal no-adjacent subspace is
$$
  X_{6}:=
  \{w\in\Omega_{6}\mid w\text{ has no adjacent }11\}.
$$
For a length-six binary path, the no-adjacent-$1$ count is the
Fibonacci count $F_{8}=21$. This is the same finite-path no-adjacent
pattern carried by the $\FibonacciCubeUp$ packet of
\autoref{ch:concrete-instances-fibonaccicube-namecert}.
\end{definition}

\begin{corollary}[Two parallel $64$-to-$21$ readings]
\label{cor:philosophy-two-parallel-sixty-four-to-twenty-one-readings}
The window-six no-adjacent target and the standard genetic-code bridge
share the same coarse source-and-class count:
$$
\begin{aligned}
  \text{window-six fold:}\quad
    &64\ \text{binary source positions}
      \rightsquigarrow 21\ \text{no-adjacent window types},\\
  \text{standard genetic code:}\quad
    &64\ \text{codons}
      \rightsquigarrow
      20\ \text{amino-acid classes}+1\ \text{stop class}.
\end{aligned}
$$
This is a count-and-window analogy. It is not equality of classifiers or
equality of fiber ledgers.
\end{corollary}

\concretizedIn{ch:concrete-instances-codon-six-bit-window-namecert}{The codon source atlas is realized as a six-coordinate BoolUp finite-window NameCert packet with Flat6 readback.}

\begin{theorem}[The two $64$-to-$21$ ledgers are not the same table]
\label{thm:philosophy-window-six-genetic-code-not-same-table}
The window-six fold and the standard genetic-code translation
classifier are not the same map.
\end{theorem}
\begin{proof}
The window-six fold is a finite binary-window classifier whose target is
the no-adjacent finite-path surface $X_{6}$. The standard genetic-code
translation classifier is an external biological bridge from codons to
amino-acid classes plus a stop class. Even when both displays have
source size $64$ and target-class count $21$, their fibers are governed
by different ledgers: the window fold records its own finite binary
collision rows, while the genetic code records biological degeneracy
rows, including singleton, doublet, triplet, quartet, and sextet
amino-acid classes in the standard table. A shared count therefore does
not license identity of maps.
\end{proof}

\begin{theorem}[Global no-$11$ is not the stop-codon classifier]
\label{thm:philosophy-global-no-eleven-not-stop-classifier}
The standard stop codons are not obtained by applying the global
no-adjacent-$11$ predicate to the entire flattened six-bit codon.
\end{theorem}
\begin{proof}
By \autoref{def:philosophy-rna-two-axis-binary-display}, the relevant
flattened strings are
$$
\begin{aligned}
  \mathrm{UAA} &\longmapsto 001010,\\
  \mathrm{UAG} &\longmapsto 001011,\\
  \mathrm{UGA} &\longmapsto 001110,\\
  \mathrm{UGG} &\longmapsto 001111.
\end{aligned}
$$
The string $001010$ has no adjacent $11$, but $001011$, $001110$, and
$001111$ do contain adjacent $11$. Thus a global no-adjacent predicate
on $\Omega_{6}$ would keep only $\mathrm{UAA}$ among the three standard
stop codons. The stop-codon reconstruction of
\autoref{thm:philosophy-three-stop-reconstruction} instead applies the
no-$11$ motif locally to the family suffix in the
$\mathrm{U}+\mathrm{RR}$ square.
\end{proof}

\begin{definition}[Local suffix rule inside the six-bit atlas]
\label{def:philosophy-local-suffix-rule-inside-six-bit-atlas}
Inside the six-bit codon atlas, the stop reconstruction uses the
following typed local rule:
$$
\begin{gathered}
  \text{select the }\mathrm{U}+\mathrm{RR}\text{ sector},\\
  \text{project positions }2\text{ and }3\text{ to the family axis},\\
  \text{exclude only the suffix }11.
\end{gathered}
$$
Equivalently,
$$
  \{\mathrm{AA},\mathrm{AG},\mathrm{GA},\mathrm{GG}\}
  \longmapsto
  \{00,01,10,11\}
$$
and the Zeckendorf-legal suffixes are $00$, $01$, and $10$. The
excluded corner is $\mathrm{GG}$, so the surviving codons are
$\mathrm{UAA}$, $\mathrm{UAG}$, and $\mathrm{UGA}$.
\end{definition}

\begin{theorem}[Codon-window bridge cannot-claim boundary]
\label{thm:philosophy-codon-window-cannot-claim-boundary}
The codon-window bridge does not license any of the following claims:
\begin{itemize}
  \item that the biological genetic code is the window-six fold;
  \item that the standard translation table is obtained by quotienting
    $\Omega_{6}$ by the no-adjacent predicate;
  \item that the standard stop codons are exactly the globally
    no-adjacent flattened codons;
  \item that the equality $4^{3}=2^{6}$ supplies a biological
    derivation of codon length three;
  \item that a shared $64$-to-$21$ count identifies the two fiber
    distributions;
  \item that $\mathrm{G}=11$ in the bridge readback is the BEDC channel
    terminator.
\end{itemize}
\end{theorem}
\begin{proof}
The first five refusals follow from
\autoref{thm:philosophy-window-six-genetic-code-not-same-table} and
\autoref{thm:philosophy-global-no-eleven-not-stop-classifier}. The last
refusal follows from the layer-separation theorem
\autoref{thm:philosophy-zstop-no-channel-token-collapse}: the displayed
binary readback of a biological base and the BEDC channel terminator
occupy different typed layers.
\end{proof}

\begin{corollary}[Allowed codon-window claim]
\label{cor:philosophy-codon-window-allowed-claim}
A codon is naturally a six-bit finite window once the four DNA or RNA
bases are read as two binary axes. The window-six bridge gives the
source-space isomorphism
$$
  \mathsf{Codon64}^{\uparrow}
  \cong
  \Omega_{6},
$$
and it explains why the numbers $64$, $21$, and the no-$11$ motif are
structurally adjacent. The stop-codon theorem remains local: in the
$\mathrm{U}+\mathrm{RR}$ sector, excluding the family suffix $11$
removes $\mathrm{UGG}$ and leaves the standard stop-codon L-shape
$\{\mathrm{UAA},\mathrm{UAG},\mathrm{UGA}\}$.
\end{corollary}
