\chapter{A Concrete Naming Certificate for $\FiniteKernelCategoryUp$}
\label{ch:concrete-instances-finitekernelcategory-namecert}
\origin{ai}

The $\FiniteKernelCategoryUp$ packet records the category-shaped reading of the finite BEDC kernel as a concrete naming certificate. Its objects are finite object histories, its arrows are displayed continuation histories, its identity and composition rows are finite $\Cont$ ledgers, and its equality rows are $\hsame$ comparisons on the same displayed histories. The packet is native to $\BHist$ and does not import an external category library, quotient morphism type, or host equality of arrows.

It is the finite, displayed-history specialization of the broader kernel-category surface in \autoref{ch:concrete-instances-kernelcategory-namecert}, and it also consumes the displayed continuation-composition route of \autoref{ch:concrete-instances-unary-continuation-category-namecert}. Its object and hom readings come from the kernel-category packet, while the identity, composition, associativity, and unit ledgers repackage those rows through finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ evidence rather than importing an external category library.

\begin{definition}[Finite-kernel category carrier]
\label{def:finite-kernel-category-carrier}
A $\FiniteKernelCategoryUp$ carrier is a finite packet
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $O$ is the finite object-history row: every object is a displayed $\BHist$ object history accepted by the kernel classifier.
\item $M$ is the displayed hom-history row: a morphism from object history $a$ to object history $b$ is a finite history $f$ equipped with the displayed continuation ledger relating the endpoint histories.
\item $I$ records identity rows, one for each accepted object history, using the empty continuation ledger from the object to itself.
\item $Q$ records composition rows: for displayed hom histories $f:a\to b$ and $g:b\to c$, the composite history is accepted only through the finite $\Cont$ ledger joining the two displayed continuations.
\item $A$ records associativity ledgers comparing the two displayed threefold composites by $\hsame$ after their $\Cont$ rows are expanded.
\item $U$ records left and right unit ledgers comparing empty-continuation composites with the original displayed hom history.
\item $H$ stores the componentwise $\hsame$ transports for object histories, hom histories, identity rows, composition rows, associativity rows, and unit rows.
\item $C$ stores the $\Cont$ routes by which a consumer reads identities, composites, associativity witnesses, and unit witnesses.
\item $P$ is the $\Pkg$ provenance row naming the consumed $\BHist$, $\hsame$, $\Cont$, identity, composition, associativity, and unit ledgers.
\item $N$ is the local $\NameCert_{\FiniteKernelCategoryUp}$ registration row.
\end{enumerate}
The local classifier compares carriers only through these displayed rows. It has no coordinate for a global category universe, quotient morphisms, external functor categories, or host equality of arrows.
\end{definition}
\leanchecked{BEDC.Derived.FiniteKernelCategoryUp.FiniteKernelCategoryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite-kernel category NameCert obligations]
\label{thm:finite-kernel-category-namecert-obligations}
The local $\NameCert_{\FiniteKernelCategoryUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier habitation by the empty object history and by unary object histories with their empty-continuation identity rows;
\item classifier stability for object histories, displayed hom histories, identity ledgers, composition ledgers, associativity ledgers, and unit ledgers by componentwise $\hsame$;
\item identity exactness, requiring each identity row to be the empty $\Cont$ continuation attached to the displayed object history;
\item composition exactness, requiring every public composite to factor through the displayed $\Cont$ row named in $Q$;
\item ledger non-escape, requiring all public category reads to pass through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, excluding external category libraries and quotient morphisms.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier habitation uses the empty object history and the unary object histories already accepted by the kernel. The empty continuation gives the identity row, so the object and identity coordinates are inhabited inside the finite carrier.

Classifier stability is componentwise. Transport object histories and hom histories by the displayed $\hsame$ rows, then transport the identity, composition, associativity, and unit ledgers along the same endpoint comparisons.

Identity and composition exactness are projections of the carrier. The identity coordinate is $I$, while each composite is read through the $\Cont$ row stored in $Q$ before it can be consumed as a displayed hom history.

The non-escape row follows by inspecting $K$. Since every public route is stored in $H$, $C$, $P$, and $N$, a consumer cannot read an external category library, quotient morphism, or host arrow equality from this certificate.
\end{proof}

\begin{theorem}[Finite-kernel category object and hom boundary]
\label{thm:finite-kernel-category-object-hom-boundary}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Every accepted object read is exposed only through the object-history row $O$, and every accepted hom read is exposed only through the hom-history row $M$. Endpoint compatibility for those hom reads is guarded by the displayed $\BHist$ histories, the componentwise $\hsame$ rows in $H$, and the $\Cont$ rows in $C$.
\end{theorem}
\begin{proof}
Project the carrier $K=(O,M,I,Q,A,U,H,C,P,N)$. The carrier definition makes $O$ the only object-history coordinate and $M$ the only hom-history coordinate.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. Carrier exposure and classifier stability transport object histories and hom histories by the displayed $\hsame$ rows, while composition exactness and ledger non-escape keep every endpoint read inside the visible $\BHist$ and $\Cont$ ledgers.

Finally repack the result as a boundary statement for consumers. Since no quotient morphism type or host arrow equality occurs in $K$, object and hom reads cannot escape the displayed $O,M,H,C,P,N$ surface.
\end{proof}

\begin{theorem}[Finite-kernel category identity and composition boundary]
\label{thm:finite-kernel-category-identity-composition-boundary}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Identity reads are exactly the rows $I$, and composition reads are exactly the rows $Q$. Associativity and unit support for those reads is supplied only by $A,U,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the displayed packet. The identity coordinate is $I$ and the composition coordinate is $Q$, so the public identity and binary-composition reads are not separate host operations.

Use the obligation surface of \autoref{thm:finite-kernel-category-namecert-obligations}. Identity exactness identifies each row of $I$ with the empty $\Cont$ continuation attached to an accepted object history, and composition exactness identifies each composite with the displayed $\Cont$ ledger stored in $Q$.

Now apply \autoref{thm:finite-kernel-category-composition-laws}. The associativity and unit rows are precisely $A$ and $U$, transported by $H$ and consumed through $C$ with provenance $P$ and local name $N$.
\end{proof}

\begin{theorem}[Finite-kernel category ledger non-escape boundary]
\label{thm:finite-kernel-category-ledger-nonescape-boundary}
Every $\FunctorUp$, $\NatTransUp$, or $\CategoryUp$ consumer of an accepted $\FiniteKernelCategoryUp$ carrier receives the finite object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and local naming rows $O,M,I,Q,A,U,H,C,P,N$. It receives no quotient morphism type, host arrow equality, functor-category object, or external category library.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-kernel-category-object-hom-boundary} and \autoref{thm:finite-kernel-category-identity-composition-boundary}. Together they expose the object, hom, identity, composition, associativity, and unit rows as the concrete carrier surface.

Apply \autoref{thm:finite-kernel-category-functor-nattrans-handoff}. Functor and natural-transformation consumers read preservation and naturality data only after the finite category rows have been exported through $H,C,P,N$.

Finally apply \autoref{thm:finite-kernel-category-category-interface-handoff}. The same finite surface is the $\CategoryUp$ interface, and the carrier has no coordinate for quotient morphisms, host arrow equality, functor-category objects, or external category libraries.
\end{proof}

\begin{theorem}[Finite-kernel category composition laws]
\label{thm:finite-kernel-category-composition-laws}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. The identity, binary composition, associativity, and left and right unit laws exported by $K$ are exactly the displayed ledgers $I$, $Q$, $A$, and $U$, transported through $H$ and consumed through $C$. No category law is discharged by ambient category theory or by quotienting hom histories.
\end{theorem}
\begin{proof}
Read the law rows from \autoref{def:finite-kernel-category-carrier}. The identity law is stored in $I$, binary composition in $Q$, associativity in $A$, and the left and right unit laws in $U$.

Transport compatibility is supplied by $H$. It keeps endpoints, hom histories, and law ledgers aligned under $\hsame$, so the same displayed rows remain the law witnesses after carrier transport.

Consumer access is supplied by $C$. Since the carrier contains no ambient category object and no quotient morphism coordinate, every law exported by $K$ is one of the displayed finite ledgers.
\end{proof}

\begin{theorem}[Finite-kernel functor and natural-transformation handoff]
\label{thm:finite-kernel-category-functor-nattrans-handoff}
Every $\FunctorUp$ or $\NatTransUp$ consumer of a $\FiniteKernelCategoryUp$ carrier receives only the finite object-history row $O$, displayed hom-history row $M$, empty-continuation identities $I$, displayed $\Cont$ composites $Q$, associativity and unit ledgers $A$ and $U$, and the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance rows $H,C,P,N$. The handoff does not export host functor categories, quotient morphisms, naturality modulo external equality, or any library category object.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:finite-kernel-category-namecert-obligations}. They bind carrier habitation, classifier stability, identity exactness, composition exactness, and ledger non-escape to the same finite packet.

A $\FunctorUp$ consumer reads objects and hom histories through $O$ and $M$, then reads identity and composition preservation against $I$ and $Q$. The associativity and unit side conditions are the displayed ledgers $A$ and $U$ transported by $H$.

A $\NatTransUp$ consumer uses the same rows for component and naturality reads. The only public routes are the continuations in $C$ and the provenance in $P$ and $N$, so the handoff remains a BEDC-native certificate surface.
\end{proof}

\begin{theorem}[Finite-kernel category interface handoff]
\label{thm:finite-kernel-category-category-interface-handoff}
Every accepted $\FiniteKernelCategoryUp$ carrier exports a $\CategoryUp$-readable interface only through the displayed object-history row $O$, hom-history row $M$, identity row $I$, composition row $Q$, associativity and unit ledgers $A,U$, and structural rows $H,C,P,N$ of \autoref{def:finite-kernel-category-carrier}. Any $\FunctorUp$ or $\NatTransUp$ consumer must first read that $\CategoryUp$ boundary before it reads preservation or naturality data. The handoff exports no quotient morphism type, host equality of arrows, functor category, or external category library.
\end{theorem}
\begin{proof}
Project the finite carrier $K=(O,M,I,Q,A,U,H,C,P,N)$. The object and hom surfaces are the rows $O$ and $M$, while the public identity and composite reads are exactly $I$ and $Q$.

Use \autoref{thm:finite-kernel-category-composition-laws} for the identity, composition, associativity, and unit rows. It identifies the category laws with $I,Q,A,U$ transported through $H$ and consumed through $C$, so the $\CategoryUp$ interface is the displayed finite ledger of \autoref{ch:concrete-instances-category-namecert}.

Now apply \autoref{thm:finite-kernel-category-functor-nattrans-handoff}. A $\FunctorUp$ consumer as in \autoref{ch:concrete-instances-functor-namecert} and a $\NatTransUp$ consumer as in \autoref{ch:concrete-instances-nattrans-namecert} read only after that boundary has exposed objects, hom histories, identities, composites, associativity, and unit ledgers.

The excluded structures are not carrier coordinates. Since $K$ contains no quotient morphism type, host arrow equality, functor category, or library category object, no continuation route or provenance row can export one.
\end{proof}

\begin{theorem}[Finite-kernel category TasteGate obligation handoff]
\label{thm:finite-kernel-category-tastegate-obligation-handoff}
For an accepted $\FiniteKernelCategoryUp$ carrier
$$
K=(O,M,I,Q,A,U,H,C,P,N),
$$
the finite object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and local $\NameCert$ rows form the paper-side obligation handoff consumed by the existing TasteGate single-carrier alignment marker. Any consumer of the TasteGate row must keep the displayed category rows $O,M,I,Q,A,U,H,C,P,N$ and cannot replace them by quotient morphisms, host arrow equality, or an external category library.
\end{theorem}
\begin{proof}
Project the carrier $K=(O,M,I,Q,A,U,H,C,P,N)$. The displayed rows are exactly the object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and local naming rows named in \autoref{def:finite-kernel-category-carrier}.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. The five NameCert obligations bind habitation, classifier stability, identity exactness, composition exactness, and ledger non-escape to the same displayed rows.

Use \autoref{thm:finite-kernel-category-composition-laws} and \autoref{thm:finite-kernel-category-category-interface-handoff}. They identify the category laws and the public $\CategoryUp$ interface with $I,Q,A,U,H,C,P,N$ over the same object and hom rows $O,M$.

The TasteGate marker is attached immediately after the carrier definition, so its single-carrier alignment reads the same displayed packet. A consumer that replaces these rows by quotient morphisms, host arrow equality, or an external category library no longer consumes the $\FiniteKernelCategoryUp$ carrier.
\end{proof}

\begin{theorem}[Finite-kernel category carrier scope]
\label{thm:finite-kernel-category-carrier-scope}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Object, hom, identity, and composition reads are grounded only in the displayed rows $O,M,I,Q,A,U,H,C,P,N$: objects are read from $O$, hom histories from $M$, identities from $I$, composites from $Q$, and their law and transport support from $A,U,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier definition. The object coordinate is $O$, the hom-history coordinate is $M$, the identity coordinate is $I$, and the composition coordinate is $Q$.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. Carrier habitation and classifier stability keep object and hom reads inside finite $\BHist$ histories and componentwise $\hsame$ transport.

Next apply \autoref{thm:finite-kernel-category-composition-laws}. It identifies the category-law surface with $I,Q,A,U$ transported through $H$ and consumed through $C$.

Finally use \autoref{thm:finite-kernel-category-category-interface-handoff}. The exported category interface is the same finite packet, so no object, hom, identity, or composition read is available outside the displayed rows.
\end{proof}

\begin{theorem}[Finite-kernel category package and NameCert scope]
\label{thm:finite-kernel-category-package-namecert-scope}
For every accepted $\FiniteKernelCategoryUp$ carrier, package provenance and local naming expose exactly the BEDC rows $O,M,I,Q,A,U,H,C,P,N$. They expose no quotient morphism, host equality of arrows, functor-category object, or external category library.
\end{theorem}
\begin{proof}
Use the carrier scope of \autoref{thm:finite-kernel-category-carrier-scope}. It binds the public object, hom, identity, composition, law, transport, and continuation reads to the displayed rows.

Apply the NameCert obligations of \autoref{thm:finite-kernel-category-namecert-obligations}. The provenance row $P$ and local naming row $N$ name the same $\BHist$, $\hsame$, $\Cont$, identity, composition, associativity, and unit ledgers.

Now apply \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. Since quotient morphisms, host arrow equality, functor-category objects, and external category libraries are not coordinates of $K$, package provenance and local naming cannot expose them.
\end{proof}

\begin{theorem}[Finite-kernel category TasteGate scope]
\label{thm:finite-kernel-category-tastegate-scope}
The existing $\FiniteKernelCategoryUp$ TasteGate marker consumes the same finite packet $O,M,I,Q,A,U,H,C,P,N$. It cannot be read after replacing any row by an external category object, quotient morphism, host arrow equality, or functor-category object.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-kernel-category-tastegate-obligation-handoff}. The TasteGate handoff is explicitly the finite object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and local NameCert packet.

Use \autoref{thm:finite-kernel-category-carrier-scope} to identify the carrier rows consumed by that handoff. The same $O,M,I,Q,A,U,H,C,P,N$ rows ground every category-shaped read.

Then use \autoref{thm:finite-kernel-category-package-namecert-scope}. External category objects, quotient morphisms, host arrow equality, and functor-category objects are absent from the package and naming surface.

Therefore replacing any displayed row by one of those external objects leaves the accepted carrier. The TasteGate marker has no route from such a replacement back to $\FiniteKernelCategoryUp$.
\end{proof}

\begin{theorem}[Finite-kernel category root obligation scope]
\label{thm:finite-kernel-category-root-obligation-scope}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Its root obligation scope is exactly the BEDC object and hom boundary $O,M$, the identity and composition rows $I,Q$, the associativity and unit rows $A,U$, the componentwise $\hsame$ transports $H$, the displayed $\Cont$ consumer routes $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert$ row $N$. The scope is readable by $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ consumers only through those rows and exports no quotient morphism, host arrow equality, functor-category object, or external category library.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-kernel-category-carrier-scope}. It binds object, hom, identity, and composition reads to $O,M,I,Q,H,C,P,N$ over finite $\BHist$, $\hsame$, and $\Cont$ rows.

Apply \autoref{thm:finite-kernel-category-composition-laws}. The associativity and unit obligations are the displayed rows $A$ and $U$, transported through $H$ and consumed through $C$ with the same provenance and local name.

Finally use \autoref{thm:finite-kernel-category-ledger-nonescape-boundary} and \autoref{thm:finite-kernel-category-tastegate-scope}. Category-shaped downstream consumers receive only the finite packet surface, and the TasteGate handoff has no route back from quotient morphisms, host equality, functor-category objects, or an external category library.
\end{proof}

\begin{theorem}[Finite-kernel category scoped closure package]
\label{thm:finite-kernel-category-scoped-closure-package}
For every accepted $\FiniteKernelCategoryUp$ carrier
$$
K=(O,M,I,Q,A,U,H,C,P,N),
$$
the scoped package consists exactly of the object row $O$, hom row $M$, identity row $I$, composition row $Q$, associativity row $A$, unit row $U$, transport row $H$, continuation row $C$, provenance row $P$, and local naming row $N$. These rows are bound to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and existing $\FiniteKernelCategoryUp$ TasteGate marker. A $\CategoryUp$, $\FunctorUp$, or $\NatTransUp$ consumer may cite the root package only by preserving this whole row family.

The scoped package introduces no external category object, quotient morphism, host arrow equality, functor-category object, or ambient category library.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-kernel-category-namecert-obligations}. Carrier exposure, classifier stability, identity exactness, composition exactness, and ledger non-escape already bind $O,M,I,Q,A,U,H,C,P,N$ to the displayed finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.

Next apply \autoref{thm:finite-kernel-category-composition-laws}. It makes associativity and unit part of the same law ledger as identity and composition, transported through $H$ and consumed through $C$ with provenance $P$ and local name $N$.

Finally use \autoref{thm:finite-kernel-category-root-obligation-scope} and \autoref{thm:finite-kernel-category-tastegate-obligation-handoff}. The root scope is the exact row family read by downstream categorical consumers, and the TasteGate handoff consumes the same single-carrier packet. By \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}, no external category object or quotient morphism can replace any row.
\end{proof}

\begin{theorem}[Finite-kernel category row scope exhaustion]
\label{thm:finite-kernel-category-row-scope-exhaustion}
Let $K=(O,M,I,Q,A,U,H,C,P,N)$ be an accepted $\FiniteKernelCategoryUp$ carrier. Every root-obligation read of $K$ is exhausted by the rows $O,M,I,Q,A,U,H,C,P,N$ over the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and existing TasteGate support. In particular, object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and local naming data cannot be distributed across a larger ambient categorical carrier before a consumer reads the $\FiniteKernelCategoryUp$ root package.
\end{theorem}
\begin{proof}
First apply \autoref{thm:finite-kernel-category-root-obligation-scope}. It states that the root obligation surface is exactly the object and hom boundary, identity and composition rows, associativity and unit rows, componentwise transport, continuation, provenance, and local naming rows.

Use \autoref{thm:finite-kernel-category-root-handoff-package}. The handoff to $\CategoryUp$, $\FunctorUp$, $\NatTransUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ consumers is the single package $O,M,I,Q,A,U,H,C,P,N$, not a family of detachable ambient objects.

Now apply \autoref{thm:finite-kernel-category-category-interface-handoff} and \autoref{thm:finite-kernel-category-functor-nattrans-handoff}. Category, functor, and natural-transformation consumers read only after this finite package has exposed the row family that supports their preservation and naturality data.

The exhaustion is closed by \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. Since the carrier exports no quotient morphism, host arrow equality, functor-category object, or external category library, no additional root row remains outside the displayed package.
\end{proof}

\begin{theorem}[Finite-kernel category public consumer boundary]
\label{thm:finite-kernel-category-public-consumer-boundary}
A public consumer may treat the $\FiniteKernelCategoryUp$ root package as scoped only when it reads object, hom, identity, composition, associativity, unit, transport, continuation, provenance, local naming, and the existing TasteGate marker through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. This is the consumer boundary for $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ handoffs: the consumer receives a finite BEDC package, not a verified bridge claim and not an imported external category object.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:finite-kernel-category-scoped-closure-package}. It identifies the scoped row package and binds it to the existing TasteGate support over the displayed BEDC support rows.

Next use \autoref{thm:finite-kernel-category-row-scope-exhaustion}. A consumer that has not read all ten rows has not exhausted the root obligation surface, while a consumer that has read them has the finite package required for the downstream categorical interface.

Finally apply \autoref{thm:finite-kernel-category-category-interface-handoff} together with \autoref{thm:finite-kernel-category-functor-nattrans-handoff}. These handoffs make $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ consumers depend on the finite package before preservation or naturality data is read. The ledger non-escape theorem and TasteGate scope then exclude quotient morphisms, external category objects, aggregate bridge claims, and any imported category library from the public consumer boundary.
\end{proof}

\begin{theorem}[Finite-kernel category root handoff package]
\label{thm:finite-kernel-category-root-handoff-package}
For every accepted $\FiniteKernelCategoryUp$ carrier $K=(O,M,I,Q,A,U,H,C,P,N)$, the root handoff package to $\CategoryUp$, $\FunctorUp$, $\NatTransUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ consumers is the single package
$$
O,M,I,Q,A,U,H,C,P,N.
$$
The package first exposes the object and hom boundary, then the identity and composition ledgers, then the associativity and unit rows, and finally the transport, continuation, provenance, and local naming rows. It does not expose any consumer route that skips $P,N$ or replaces the local NameCert rows by a host category object.
\end{theorem}
\begin{proof}
Use \autoref{thm:finite-kernel-category-namecert-obligations}. The obligation surface already lists carrier habitation, classifier stability, identity exactness, composition exactness, and ledger non-escape for the same displayed rows.

Next apply \autoref{thm:finite-kernel-category-category-interface-handoff}. The $\CategoryUp$ interface is the displayed finite ledger, so every functor or natural-transformation consumer reads the object, hom, identity, composition, associativity, and unit rows before preservation or naturality data.

The package and naming rows are fixed by \autoref{thm:finite-kernel-category-package-namecert-scope}. Since $P$ and $N$ name only the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet, the root handoff cannot be detached from the local certificate.
\end{proof}

\begin{theorem}[Finite-kernel category object row totality]
\label{thm:finite-kernel-category-object-row-totality}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Every accepted object read of
$K$ factors through the displayed object-history row $O$. The factorization
keeps the object witness in the same $\BHist$ history, componentwise $\hsame$
transport row $H$, displayed $\Cont$ consumer row $C$, $\Pkg$ provenance row
$P$, and local $\NameCert$ row $N$; no category, functor, or
natural-transformation consumer can read an object of $K$ outside that
object-history row.
\end{theorem}
\begin{proof}
Read the carrier through \autoref{def:finite-kernel-category-carrier}. The
only object coordinate of the accepted packet is $O$, and its route is
presented together with the transport, continuation, provenance, and local
naming rows.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. Carrier
habitation and classifier stability bind the accepted object read to the
displayed $\BHist$ row and to the componentwise $\hsame$ transport that keeps
the same packet visible to downstream consumers.

The law rows do not create another object source. By
\autoref{thm:finite-kernel-category-composition-laws}, identity, composition,
associativity, and unit use the displayed categorical rows over the same
object boundary, and \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}
prevents replacing that boundary by host object equality, quotient objects, or
an external category library.
\end{proof}

\begin{theorem}[Finite-kernel category morphism route stability]
\label{thm:finite-kernel-category-morphism-route-stability}
For every accepted $\FiniteKernelCategoryUp$ carrier
$K=(O,M,I,Q,A,U,H,C,P,N)$, each accepted hom read and each endpoint transport
used by a $\CategoryUp$, $\FunctorUp$, or $\NatTransUp$ consumer remains inside
the displayed morphism route $M,H,C,P,N$. In particular, source and target
movement is recorded by the same componentwise $\hsame$ transport, displayed
$\Cont$ continuation, package provenance, and local name that expose the hom
history, rather than by host arrow equality or a quotient morphism.
\end{theorem}
\begin{proof}
Start from \autoref{def:finite-kernel-category-carrier}. The hom row is $M$,
and the only endpoint-transport data attached to it are the displayed rows
$H,C,P,N$.

Use \autoref{thm:finite-kernel-category-namecert-obligations}. Classifier
stability and composition exactness force hom histories and their endpoints to
travel through the same componentwise $\hsame$ and $\Cont$ rows before the
packet is consumed.

The category-law surface preserves that route. Apply
\autoref{thm:finite-kernel-category-composition-laws} to keep identity,
composition, associativity, and unit reads over the same hom and endpoint
rows, then use \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}
to exclude any replacement by host arrows, quotient morphisms, or external
categorical equality.
\end{proof}

\begin{theorem}[Finite-kernel category composition ledger nonescape]
\label{thm:finite-kernel-category-composition-ledger-nonescape}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Every identity, composition,
associativity, or unit consumer reads only the displayed ledger rows
$I,Q,A,U,H,C,P,N$. These consumers cannot replace the ledger by quotient
morphisms, host arrow equality, functor-category equality, or an external
category-library proof of the same laws.
\end{theorem}
\begin{proof}
Project the ledger coordinates of \autoref{def:finite-kernel-category-carrier}.
Identities are carried by $I$, composites by $Q$, associativity by $A$, and
unit laws by $U$, all with the same transport, continuation, provenance, and
local naming rows.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. Identity
exactness, composition exactness, and ledger non-escape are obligations of the
same local NameCert surface, so a law consumer cannot detach $I,Q,A,U$ from
$H,C,P,N$.

Finally use \autoref{thm:finite-kernel-category-composition-laws}. It makes
the displayed identity, composition, associativity, and unit rows the law
surface consumed by categorical readers. The boundary theorem,
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary}, rules out a
second route through quotient morphisms, host arrow equality, or an ambient
category library.
\end{proof}

\begin{theorem}[Finite-kernel category root downstream unblock]
\label{thm:finite-kernel-category-root-downstream-unblock}
Every downstream categorical consumer that asks for a finite BEDC category, functor source, natural-transformation source, or TasteGate handoff from $\FiniteKernelCategoryUp$ is unblocked by the root package
$$
O,M,I,Q,A,U,H,C,P,N
$$
provided it consumes the object and hom boundary, identity and composition rows, ledger non-escape clause, and TasteGate handoff together. A consumer that omits one of these rows has not consumed the $\FiniteKernelCategoryUp$ root obligation surface.
\end{theorem}
\begin{proof}
First build the categorical boundary. Apply \autoref{thm:finite-kernel-category-root-obligation-scope} to obtain the exact object, hom, identity, composition, associativity, unit, transport, continuation, provenance, and naming surface.

Next build the handoff package. Apply \autoref{thm:finite-kernel-category-root-handoff-package}; it orders the $\CategoryUp$, $\FunctorUp$, $\NatTransUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ reads through the same finite rows.

Finally compose with \autoref{thm:finite-kernel-category-tastegate-obligation-handoff}. The TasteGate side consumes the same single-carrier packet, so a downstream route that preserves all listed rows is unblocked, while a route omitting object/hom data, identity/composition data, ledger non-escape, or TasteGate handoff leaves the root obligation surface.
\end{proof}

\begin{theorem}[Finite-kernel category downstream root package]
\label{thm:finite-kernel-category-downstream-root-package}
For every accepted $\FiniteKernelCategoryUp$ carrier $K=(O,M,I,Q,A,U,H,C,P,N)$, the downstream root package for $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ consumers is exactly the displayed row sequence
$$
O,M,I,Q,A,U,H,C,P,N.
$$
It consists of the object and hom boundary, identity and composition rows, associativity and unit rows, componentwise $\hsame$ transport, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row. No downstream categorical consumer receives a smaller root package by replacing those rows with quotient morphisms, host arrow equality, functor-category objects, or an external category library.
\end{theorem}
\begin{proof}
Start with the root obligation scope, \autoref{thm:finite-kernel-category-root-obligation-scope}. It identifies $O,M,I,Q,A,U,H,C,P,N$ as the complete finite surface read by $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ consumers.

Next apply the root handoff package and category interface handoff. Theorem~\ref{thm:finite-kernel-category-root-handoff-package} orders the object, hom, identity, composition, law, transport, continuation, provenance, and naming rows, while \autoref{thm:finite-kernel-category-category-interface-handoff} makes the same rows the categorical interface for downstream reads.

Finally use \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. Since the ledger boundary exports no quotient morphism, host arrow equality, functor-category object, or external category library, the downstream package is exactly the displayed row sequence and not a larger ambient categorical object.
\end{proof}

\begin{theorem}[Finite-kernel category hom endpoint transport determinacy]
\label{thm:finite-kernel-category-hom-endpoint-transport-determinacy}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Any accepted hom-history
read transported by componentwise $\hsame$ preserves the displayed source and
target object rows named by the same packet. A $\FunctorUp$ or $\NatTransUp$
consumer cannot reuse the hom row $M$ with different endpoints unless it also
transports the corresponding object rows through the same $H,C,P,N$ packet.
\end{theorem}
\begin{proof}
Start with the object and hom boundary,
\autoref{thm:finite-kernel-category-object-hom-boundary}. It makes the object
rows $O$ and hom rows $M$ the only displayed endpoints and arrows available
to a category-shaped consumer.

Apply the identity and composition boundary together with the composition
laws, \autoref{thm:finite-kernel-category-identity-composition-boundary} and
\autoref{thm:finite-kernel-category-composition-laws}. Identities and
composites are stored in $I,Q,A,U$ only after their source and target object
rows have been kept aligned through the same transport and continuation
surface.

Finally use the category interface handoff and ledger non-escape boundary,
\autoref{thm:finite-kernel-category-category-interface-handoff} and
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. A functor or
natural-transformation reader therefore receives endpoint data only as part
of the displayed $O,M,I,Q,A,U,H,C,P,N$ packet. Reusing $M$ with different
endpoints would require an extra host arrow equality or quotient morphism,
and those coordinates are not exported by the carrier.
\end{proof}

\begin{theorem}[Finite-kernel categorical row readback]
\label{thm:finite-kernel-category-category-functor-nattrans-row-readback}
Let
$$
K=(O,M,I,Q,A,U,H,C,P,N)
$$
be an accepted $\FiniteKernelCategoryUp$ carrier. Every $\CategoryUp$,
$\FunctorUp$, or $\NatTransUp$ readback of $K$ factors through exactly the
displayed rows $O,M,I,Q,A,U,H,C,P,N$: category reads consume object, hom,
identity, composition, associativity, and unit rows; functor reads consume the
same rows before preservation data; natural-transformation reads consume the
same rows before component and naturality data. No readback may replace those
rows by quotient morphisms, host arrow equality, a functor-category object, or
an external category library.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-kernel-category-carrier}. The
accepted packet has only the rows $O,M,I,Q,A,U,H,C,P,N$ available for
categorical consumers.

Apply the category interface handoff,
\autoref{thm:finite-kernel-category-category-interface-handoff}. It makes
$O,M,I,Q,A,U,H,C,P,N$ the $\CategoryUp$-readable boundary and forces
$\FunctorUp$ and $\NatTransUp$ consumers to read that boundary first.

Use the functor and natural-transformation handoff together with the ledger
non-escape theorem, \autoref{thm:finite-kernel-category-functor-nattrans-handoff}
and \autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. The
handoff supplies no quotient morphism, host equality, functor-category object,
or external library coordinate, so every readback factors through exactly the
finite BEDC row sequence.
\end{proof}

\begin{theorem}[Finite-kernel functor identity preservation]
\label{thm:finite-kernel-category-functor-identity-preservation}
Every $\FunctorUp$ consumer of an accepted $\FiniteKernelCategoryUp$ carrier
$K=(O,M,I,Q,A,U,H,C,P,N)$ preserves the displayed identity row $I$ through the
same object, hom, identity, composition, associativity, unit, transport,
continuation, provenance, and naming rows $O,M,I,Q,A,U,H,C,P,N$. The
preservation obligation is a BEDC row obligation and is not discharged by a
quotient morphism, host arrow equality, external category library, or
functor-category object.
\end{theorem}
\begin{proof}
Start with the category, functor, and natural-transformation readback theorem,
\autoref{thm:finite-kernel-category-category-functor-nattrans-row-readback}.
It makes the accepted consumer read the finite row sequence
$O,M,I,Q,A,U,H,C,P,N$ rather than an ambient category object.

Apply the functor and natural-transformation handoff,
\autoref{thm:finite-kernel-category-functor-nattrans-handoff}. A
$\FunctorUp$ consumer can inspect identity preservation only after the
identity row $I$ has been exported with the carrier rows that determine its
source and target histories.

Finally use the composition provenance factorization and ledger non-escape
boundary,
\autoref{thm:finite-kernel-category-composition-provenance-factorization} and
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. The
provenance and local naming rows keep the preservation witness inside the
displayed BEDC packet, so no quotient or host equality route can replace $I$.
\end{proof}

\begin{theorem}[Finite-kernel functor composition preservation]
\label{thm:finite-kernel-category-functor-composition-preservation}
Every $\FunctorUp$ consumer of an accepted $\FiniteKernelCategoryUp$ carrier
$K=(O,M,I,Q,A,U,H,C,P,N)$ preserves the displayed composition row $Q$ through
the same row sequence $O,M,I,Q,A,U,H,C,P,N$. Composition preservation may use
the associativity row $A$, the unit row $U$, componentwise transport $H$,
continuation consumption $C$, provenance $P$, and local naming $N$, but it has
no separate quotient morphism, host arrow equality, external category library,
or functor-category object.
\end{theorem}
\begin{proof}
Read the accepted consumer through
\autoref{thm:finite-kernel-category-category-functor-nattrans-row-readback}.
The composition preservation input is the displayed row $Q$ in the same packet
as $O,M,I,A,U,H,C,P,N$.

Use \autoref{thm:finite-kernel-category-composition-provenance-factorization}.
It factors composition, associativity, and unit consumption through
$Q,A,U,H,C,P,N$, so a functor cannot preserve composition by bypassing the
provenance row or the local $\NameCert$ row.

Now apply \autoref{thm:finite-kernel-category-functor-nattrans-handoff} and
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. The handoff
exports the displayed category-law rows to $\FunctorUp$ consumers, and the
boundary excludes quotient morphisms, host equality, external category
libraries, and functor-category objects from the preservation surface.
\end{proof}

\begin{theorem}[Finite-kernel natural-transformation square boundary]
\label{thm:finite-kernel-category-natural-transformation-square-boundary}
Every $\NatTransUp$ consumer of an accepted $\FiniteKernelCategoryUp$ carrier
$K=(O,M,I,Q,A,U,H,C,P,N)$ reads the naturality square boundary through the
displayed object row $O$, hom row $M$, identity row $I$, composition row $Q$,
associativity and unit rows $A,U$, componentwise transport $H$, continuation
row $C$, provenance row $P$, and local naming row $N$. The square has no
boundary edge supplied by quotient morphisms, host arrow equality, an external
category library, or a functor-category object.
\end{theorem}
\begin{proof}
Begin with the readback theorem,
\autoref{thm:finite-kernel-category-category-functor-nattrans-row-readback}.
It routes $\NatTransUp$ consumers through the finite row sequence, so the
naturality square boundary is assembled from displayed object and hom histories
and their identity and composition rows.

Apply the functor and natural-transformation handoff,
\autoref{thm:finite-kernel-category-functor-nattrans-handoff}. The handoff
places naturality inspection after the category rows $O,M,I,Q,A,U$ and their
transport, continuation, provenance, and naming rows have been exported.

Finish with composition provenance factorization and ledger non-escape,
\autoref{thm:finite-kernel-category-composition-provenance-factorization} and
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary}. These results
keep every boundary edge inside $O,M,I,Q,A,U,H,C,P,N$ and block any external
category-library or functor-category replacement.
\end{proof}

\begin{theorem}[Finite-kernel composition provenance factorization]
\label{thm:finite-kernel-category-composition-provenance-factorization}
For every accepted $\FiniteKernelCategoryUp$ carrier $K=(O,M,I,Q,A,U,H,C,P,N)$,
composition, associativity, and unit consumption factor through the composition
row $Q$, associativity row $A$, unit row $U$, componentwise transport row $H$,
displayed continuation row $C$, package provenance row $P$, and local
$\NameCert$ row $N$. A consumer cannot skip the provenance row or the local
NameCert row while still consuming the category-law surface of $K$.
\end{theorem}
\begin{proof}
Start with the law rows of \autoref{def:finite-kernel-category-carrier}. The
composition row is $Q$, associativity is recorded in $A$, and the left and
right unit laws are recorded in $U$.

Apply the composition laws,
\autoref{thm:finite-kernel-category-composition-laws}. They require the law
rows to be transported through $H$ and consumed through $C$, so the laws are
not detached from the displayed packet.

Finally use the interface handoff and hom endpoint transport determinacy,
\autoref{thm:finite-kernel-category-category-interface-handoff} and
\autoref{thm:finite-kernel-category-hom-endpoint-transport-determinacy}. These
force categorical consumers to keep endpoints, hom histories, law rows,
provenance, and local naming in the same $Q,A,U,H,C,P,N$ factorization.
\end{proof}

\begin{theorem}[Finite-kernel bridge consumer nonescape]
\label{thm:finite-kernel-category-bridge-consumer-nonescape}
Every bridge-facing categorical consumer of an accepted $\FiniteKernelCategoryUp$
carrier receives only the finite BEDC packet
$$
O,M,I,Q,A,U,H,C,P,N.
$$
It receives no quotient morphism, host arrow equality, functor-category object,
external category library, or bridge route that reads category, functor, or
natural-transformation data outside the displayed rows.
\end{theorem}
\begin{proof}
First read the carrier and category interface through
\autoref{def:finite-kernel-category-carrier} and
\autoref{thm:finite-kernel-category-category-interface-handoff}. The bridge
consumer starts from the same object, hom, identity, composition,
associativity, unit, transport, continuation, provenance, and naming rows.

Next apply \autoref{thm:finite-kernel-category-functor-nattrans-handoff}. It
keeps functor and natural-transformation consumers on the same finite row
sequence before preservation, components, or naturality are inspected.

Finish with the ledger non-escape boundary and endpoint determinacy,
\autoref{thm:finite-kernel-category-ledger-nonescape-boundary} and
\autoref{thm:finite-kernel-category-hom-endpoint-transport-determinacy}. Since
the carrier has no quotient, host equality, functor-category, or external
library coordinate, a bridge-facing consumer cannot export one.
\end{proof}

\begin{theorem}[Finite-kernel category carrier habitation scope]
\label{thm:finite-kernel-category-carrier-habitation-scope}
For an accepted $\FiniteKernelCategoryUp$ carrier
$$
K=(O,M,I,Q,A,U,H,C,P,N),
$$
carrier habitation is grounded exactly by the finite object-history row $O$,
the displayed hom-history row $M$, the empty-continuation identity row $I$,
and the local $\NameCert$ row $N$. The habitation witness uses no quotient
morphism, host category object, ambient arrow equality, or external category
library object.
\end{theorem}
\begin{proof}
Start from the carrier coordinates in
\autoref{def:finite-kernel-category-carrier}. The object carrier is presented
by finite $\BHist$ histories in $O$, the hom carrier by displayed histories in
$M$, identities by the empty $\Cont$ continuations recorded in $I$, and local
naming by $N$.

Use the obligation surface of
\autoref{thm:finite-kernel-category-namecert-obligations}. Its habitation row
binds those object, hom, identity, and local naming coordinates to the same
finite packet, so there is no second carrier source to read.

Finally apply the root obligation boundary,
\autoref{thm:finite-kernel-category-root-obligation-scope}. That boundary
exports only $O,M,I,Q,A,U,H,C,P,N$ to categorical consumers; quotient
morphisms, host category objects, and ambient category-library objects are not
coordinates of the accepted carrier.
\end{proof}

\begin{theorem}[Finite-kernel category classifier stability scope]
\label{thm:finite-kernel-category-classifier-stability-scope}
For an accepted $\FiniteKernelCategoryUp$ carrier
$$
K=(O,M,I,Q,A,U,H,C,P,N),
$$
classifier transport is exactly the componentwise $\hsame$ row $H$ over the
object, hom, identity, composition, associativity, and unit ledgers. The
transport is consumed only through the displayed continuation row $C$, the
package provenance row $P$, and the local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Read the classifier coordinates from
\autoref{def:finite-kernel-category-carrier}. The row $H$ is the
componentwise $\hsame$ transport for the displayed object and hom histories
and for the ledger rows that depend on them.

Use \autoref{thm:finite-kernel-category-composition-laws} to identify the
dependent law surface. Identity, composition, associativity, and unit reads
are the rows $I,Q,A,U$, so classifier stability acts on the full law ledger
rather than on a detached ambient category object.

Now apply \autoref{thm:finite-kernel-category-namecert-obligations} and
\autoref{thm:finite-kernel-category-root-obligation-scope}. The same
componentwise transport is consumed through $C$ and named through $P,N$; no
consumer receives an alternate classifier route outside $\Cont$, $\Pkg$, and
\NameCert.
\end{proof}

\begin{theorem}[Finite-kernel category identity-composition exactness scope]
\label{thm:finite-kernel-category-identity-composition-exactness-scope}
For an accepted $\FiniteKernelCategoryUp$ carrier
$$
K=(O,M,I,Q,A,U,H,C,P,N),
$$
identity exactness is the row $I$ and composition exactness is the row $Q$.
Associativity and unit support enter only through $A$ and $U$, transported by
$H$, consumed through $C$, recorded by $P$, and named locally by $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-kernel-category-carrier}. The
identity row is $I$, and the composition row is $Q$; both are displayed BEDC
rows over the same object and hom histories.

Apply \autoref{thm:finite-kernel-category-namecert-obligations}. Its
identity-exactness and composition-exactness obligations attach $I$ and $Q$
to the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
packet.

Finally use \autoref{thm:finite-kernel-category-composition-laws} and
\autoref{thm:finite-kernel-category-root-obligation-scope}. Associativity and
unit support are precisely $A,U,H,C,P,N$, so exactness cannot be discharged by
an external composition law or by a quotient morphism outside the displayed
carrier.
\end{proof}

\begin{theorem}[Finite-kernel displayed source totality]
\label{thm:finite-kernel-category-displayed-source-totality}
Every accepted finite-kernel category consumer must display the complete row
family
$$
O,M,I,Q,A,U,H,C,P,N
$$
of the carrier $K=(O,M,I,Q,A,U,H,C,P,N)$. The object and hom rows are read over
finite $\BHist$ histories, the identity, composition, associativity, and unit
rows are read through $\hsame$ and $\Cont$, the provenance row is read through
$\Pkg$, and the local naming row is read through $\NameCert$. No downstream
$\CategoryUp$, $\FunctorUp$, or $\NatTransUp$ consumer has accepted the root
package until all ten rows are displayed together.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-kernel-category-carrier}. Its
visible source is the ten-row packet $O,M,I,Q,A,U,H,C,P,N$, with no separate
coordinate for a host category object or a quotient morphism carrier.

Apply the NameCert obligations,
\autoref{thm:finite-kernel-category-namecert-obligations}. They bind carrier
habitation, classifier stability, identity exactness, composition exactness,
and ledger non-escape to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows.

Finally use the root obligation scope,
\autoref{thm:finite-kernel-category-root-obligation-scope}. It identifies that
same displayed row family as the only source package exported to categorical
consumers, so a partial row read is not an accepted $\FiniteKernelCategoryUp$
consumer read.
\end{proof}

\begin{theorem}[Finite-kernel composite ledger determinacy]
\label{thm:finite-kernel-category-composite-ledger-determinacy}
Let $K=(O,M,I,Q,A,U,H,C,P,N)$ be an accepted $\FiniteKernelCategoryUp$ carrier.
If two composite reads have the same displayed object rows $O$, hom rows $M$,
identity row $I$, composition row $Q$, continuation row $C$, provenance row
$P$, and local naming row $N$, then they determine the same public ledger read
of $K$. The determinacy is internal to the displayed carrier: it uses the
composition ledger nonescape boundary and the identity-composition exactness
scope, not an external category-library equality.
\end{theorem}
\begin{proof}
First read the two composites through the displayed carrier. The shared object
and hom rows fix the endpoints, while the shared identity and composition rows
fix the BEDC-native law surface.

Apply the identity-composition exactness scope,
\autoref{thm:finite-kernel-category-identity-composition-exactness-scope}. It
identifies identity exactness with $I$ and composition exactness with $Q$, with
associativity, unit, transport, continuation, provenance, and naming supplied by
the same packet.

Finish with the composition ledger nonescape theorem,
\autoref{thm:finite-kernel-category-composition-ledger-nonescape}. Since a
public composite cannot leave $Q,C,P,N$ for a quotient morphism, host arrow
equality, or external category object, the two reads expose the same public
ledger.
\end{proof}

\begin{theorem}[Finite-kernel natural-transformation consumer scope]
\label{thm:finite-kernel-category-nattrans-consumer-scope}
The downstream $\CategoryUp$, $\FunctorUp$, and $\NatTransUp$ consumers may read
the $\FiniteKernelCategoryUp$ root package only through the full displayed row
family
$$
O,M,I,Q,A,U,H,C,P,N
$$
together with the existing $\FiniteKernelCategoryUp$ TasteGate marker. They may
not read it through quotient morphisms, host arrow equality, functor-category
objects, or an external category library.
\end{theorem}
\begin{proof}
Start with the displayed source totality theorem,
\autoref{thm:finite-kernel-category-displayed-source-totality}. It forces every
accepted downstream consumer to display the complete ten-row source package
over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next apply the TasteGate handoff,
\autoref{thm:finite-kernel-category-tastegate-obligation-handoff}. The existing
TasteGate marker consumes the same single-carrier alignment, so the consumer
scope includes that marker only as a read of the displayed package.

Finally use the category, functor, and natural-transformation readback theorem,
\autoref{thm:finite-kernel-category-category-functor-nattrans-row-readback}.
It routes all three downstream consumers through the same finite row sequence
and excludes quotient morphisms, host arrow equality, functor-category objects,
and external category libraries from the public read.
\end{proof}
