\section{Scientific Inquiry, Consciousness-Like Reflection, and T-Supply Boundaries}
\label{sec:scientific-inquiry-conscious-reflection-t-supply}
\origin{ai}

\begin{remark}[Vision seed status]
\label{rem:scientific-inquiry-conscious-t-vision-seed-status}
This interface has vision-seed status: it is a schema horizon and has no
Lean target. It is not a finite-kernel theorem. It records the comparison
shape a later development would have to close before scientific inquiry,
consciousness-like reflection, or $\mathsf{T}$-supply exposure could be
reported as BEDC theorems about reality.

The interface uses the current BEDC readings that observer identity is
internal to $\Hist$, that $\Cont$ has only history-valued arguments, that
observation, distinction, and local time-step share the same continuation
form, that consciousness enters the object layer only as a records-side
carrier, and that $\mathsf{T}$ is a non-internalizable forward-supply
position. It therefore refuses the primitive equations
$$
\mathsf{Science}=\mathsf{Consciousness},
\qquad
\mathsf{Science}=\mathsf{T},
\qquad
\mathsf{Consciousness}=\mathsf{T}.
$$
The safe reading is instead
$$
\mathsf{Science}
=
\mathsf{PublicLedgeredMode}
\bigl(\mathsf{ConsciousnessLikeReflection}(\mathsf{HistTime})\bigr).
$$
Scientific inquiry may be consciousness-like because it can read,
classify, and reuse its own observation traces. It is not consciousness
itself, because a consciousness reading is the focused records-side
carrier of \autoref{def:philosophy-conscious-record}, while scientific
inquiry adds public signatures, model-generated signatures, classifiers,
stability, descent, provenance, and failure surfaces. It is not
$\mathsf{T}$, because $\mathsf{T}$ is not an object, state, record, rule,
axiom, model, or scientific theory. Scientific inquiry exposes
$\mathsf{T}$-supply sockets whenever finite records are asked to bind
future lawlike truth beyond their displayed witnesses; it does not
internalize the supply position.
\end{remark}

\begin{definition}[Consciousness-like reflection]
\label{def:consciousness-like-reflection}
Let $L_N$ be a finite focused multi-$\Hist$ ledger and let $F$ be its
focus. A records-side process $P$ is \emph{consciousness-like} relative
to $(L_N,F)$ when $P$ factors through the focused carrier
$$
\mathsf{ConsciousRecord}(L_N,F)=(H(F),\Theta(F),S(F),\rho),
$$
and later rows of $P$ may use the focused generated history $H(F)$, its
local continuation trace $\Theta(F)$, its selector ledger $S(F)$, and its
endpoint or trace self-proxy $\rho$ as source material for readback,
comparison, or further inscription. This is a structural records-side
condition. It is not an object-level definition of phenomenal essence
and it adds no subject-substance.
\end{definition}

\begin{definition}[Public scientific reflection]
\label{def:public-scientific-reflection}
Let $A=(M,R,\Pi)$ be a physical audit target, with $M$ a mathematical,
computational, or conceptual model, $R$ a target phenomenon or system,
and $\Pi$ an observation bundle. A \emph{public scientific reflection}
over $A$ and $(L_N,F)$ is a finite ledger-readable packet
$$
\mathsf{SciRef}_{N}
=
(\mathsf{CR},
\mathsf{Source},
\mathsf{ObsSig},
\mathsf{ModSig},
C,
\mathsf{Tower},
D,
L,
\Phi,
\mathsf{Strength}),
$$
where $\mathsf{CR}=\mathsf{ConsciousRecord}(L_N,F)$;
$\mathsf{Source}$ records finite source traces drawn from or related to
$\mathsf{CR}$; $\mathsf{ObsSig}$ records observed signatures generated
under $\Pi$; $\mathsf{ModSig}$ records model-generated signatures exposed
by $M$; $C$ is the classifier of fit between $\mathsf{ObsSig}$ and
$\mathsf{ModSig}$; $\mathsf{Tower}$ records the approximation path from
source traces to public model use; $D$ records stability and descent
obligations; $L$ records provenance, compression, hidden residue,
idealization, and translation data; $\Phi$ is the failure surface; and
$\mathsf{Strength}$ records the strongest justified audit strength.

The packet is public when its visible claims are classifier-stable,
reproducible or transportable through stated inter-$\Hist$ relation rows,
and failure-exposed. A private readback of a focused trace is therefore
not yet science. It becomes scientific only when it is externalized as
source, signature, classifier, stability, descent, ledger, and
failure-surface data.
\end{definition}

\begin{definition}[T-supply exposure by scientific inquiry]
\label{def:t-supply-exposure-by-scientific-inquiry}
A public scientific reflection exposes a $\mathsf{T}$-supply socket when
a finite prefix of $\mathsf{SciRef}_{N}$ is asked to license a
forward-binding claim not generated by the displayed records, closed
inductive generators, naming-certificate fields, or certified
continuation laws. Typical scientific cases include universal lawlike
reuse, prediction beyond the observed source horizon, open-ended
induction, cross-regime extrapolation, and claims of final explanation.

Such exposure is admissible only as a socketed ledger row: the missing
shape, consumption site, intended claim strength, and preventing audit
gate must be stated. The socket records the boundary. It does not turn
$\mathsf{T}$ into a model component or a hidden scientific axiom.
\end{definition}

\begin{proposition}[Focused source readback is consciousness-like]
\label{prop:scientific-inquiry-conscious-like-when-focused}
In a fixed context where the source traces of $\mathsf{SciRef}_{N}$
factor through $\mathsf{ConsciousRecord}(L_N,F)$, scientific inquiry is
consciousness-like reflection.
\end{proposition}

\begin{proof}
By definition, the source material of $\mathsf{SciRef}_{N}$ is drawn from
or related to
$$
\mathsf{CR}=(H(F),\Theta(F),S(F),\rho).
$$
The observed signatures, model comparison rows, classifier witnesses, and
later ledger rows reuse that finite trace material as public source data.
Thus the scientific packet performs readback on focused Hist-time traces
and records the result as further rows. This is exactly the structural
condition of consciousness-like reflection relative to $(L_N,F)$. No
subject parameter is added, since all rows factor through the focused
history, continuation trace, selector ledger, self-proxy, and public
certificate fields.
\end{proof}

\begin{proposition}[Scientific inquiry is not consciousness itself]
\label{prop:scientific-inquiry-not-consciousness-itself}
Scientific inquiry is not identical with $\mathsf{ConsciousRecord}(L_N,F)$.
\end{proposition}

\begin{proof}
$\mathsf{ConsciousRecord}(L_N,F)$ has the four records-side components
$H(F)$, $\Theta(F)$, $S(F)$, and $\rho$. A public scientific reflection
requires additional fields: source-trace exposure, observed signatures,
model-generated signatures, a fit classifier, an approximation tower,
stability and descent obligations, a provenance ledger, a failure
surface, and an audit-strength row. These fields are not supplied by
every consciousness reading. Conversely, a focused conscious record may
exist without any model family, public classifier, reproducibility row,
or failure surface. Therefore scientific inquiry can be a public mode of
consciousness-like reflection, but it is not consciousness itself.
\end{proof}

\begin{corollary}[No de-indexed consciousness-science predicate]
\label{cor:no-deindexed-consciousness-science-predicate}
The schema licenses only context-indexed judgments such as
$$
\mathsf{SciRef}^{A}_{N}(L_N,F),
\qquad
\mathsf{ConsciousLike}_{N}(L_N,F),
\qquad
\mathsf{PublicFit}^{A}_{N}(L_N,F),
\qquad
\mathsf{Lawlike}^{A}_{N}(L_N,F).
$$
It does not license a context-free predicate
$\mathsf{Science}=\mathsf{Consciousness}$.
\end{corollary}

\begin{proof}
Removing the indices removes the focused ledger, focus,
observer-history, trace, selector ledger, self-proxy, model, target
phenomenon, observation bundle, classifier, stability and descent
obligations, ledger, failure surface, and audit strength. BEDC supplies
no global observer, no global clock, no hidden subject carrier, and no
context-free classifier capable of replacing these fields.
\end{proof}

\begin{proposition}[Scientific inquiry is not T]
\label{prop:scientific-inquiry-not-t}
Scientific inquiry is not identical with the transcendental supply
position $\mathsf{T}$.
\end{proposition}

\begin{proof}
A scientific reflection is a finite ledger-readable packet: its public
standing depends on source rows, signature rows, classifier rows,
stability and descent rows, provenance rows, failure-surface rows, and
audit-strength rows. Thus it is an object-layer or certificate-layer
construction. By \autoref{def:transcendental-input-supply-position},
$\mathsf{T}$ is the structural position from which forward-binding supply
enters a closed observational system; it is not an observation state, not
a record, not a closed-generation rule, not a substrate axiom, and not an
object-layer carrier. Identifying scientific inquiry with $\mathsf{T}$
would internalize the supply position as a scientific object or theory.
That is exactly what the $\mathsf{T}$-boundary and audit gates refuse.
\end{proof}

\begin{corollary}[T-sockets do not make the scientist T]
\label{cor:t-sockets-do-not-make-scientist-t}
A scientific inquiry may expose $\mathsf{T}$-supply sockets without being
$\mathsf{T}$, and a conscious record may be an inscription point without
being $\mathsf{T}$.
\end{corollary}

\begin{proof}
Socket exposure marks a missing forward-binding discharge and the gate
that prevents its internalization. Inscription records the local site at
which durable records enter a closed observational history. Neither
operation supplies the far-end supply position as an internal object.
They record where the boundary is encountered.
\end{proof}

\begin{proposition}[Science is public consciousness-like reflection]
\label{prop:science-public-consciousness-like-reflection}
Within this vision-seed schema, scientific inquiry is the public,
classifier-governed, failure-exposed mode of consciousness-like Hist-time
reflection.
\end{proposition}

\begin{proof}
Consciousness-like reflection supplies the focused readback surface:
generated history, local continuation trace, selector ledger, and
self-proxy. Scientific reflection adds the public audit discipline:
source traces, observed signatures, model-generated signatures, classifier
of fit, approximation tower, stability domain, descent obligations,
provenance ledger, failure surface, and audit strength. The resulting
packet is therefore neither a bare private conscious record nor a
transcendental supply position. It is focused Hist-time reflection
disciplined into public certificate form.
\end{proof}

\begin{corollary}[Safe and unsafe compressed readings]
\label{cor:safe-unsafe-conscious-science-t-readings}
The safe compressed readings are
$$
\mathsf{Consciousness}
=
\mathsf{FocusedSelfProxy}(\mathsf{HistTime}),
\qquad
\mathsf{Science}
=
\mathsf{PublicLedgeredReflection}(\mathsf{HistTime}),
\qquad
\mathsf{T}
=
\mathsf{NonInternalizableForwardSupplyPosition},
$$
or, more sharply,
$$
\mathsf{Science}
=
\mathsf{PublicLedgeredMode}
\bigl(\mathsf{ConsciousnessLikeReflection}(\mathsf{HistTime})\bigr).
$$
The unsafe promotions are
$$
\mathsf{Science}=\mathsf{Consciousness},
\qquad
\mathsf{Science}=\mathsf{T},
\qquad
\mathsf{Consciousness}=\mathsf{T}.
$$
\end{corollary}

\begin{proof}
The safe readings preserve the required indices and certificate layers.
The unsafe promotions erase the difference between records-side focused
carrier, public scientific audit packet, and non-internalizable supply
position.
\end{proof}

\begin{remark}[Reading]
\label{rem:scientific-inquiry-conscious-t-reading}
Scientific inquiry is not consciousness as such, but consciousness-like
reflection disciplined into a public ledger. A focused conscious record
can read itself; scientific method makes such readback reproducible,
classifier-visible, model-comparable, stability-indexed, and
failure-exposed. A scientific law is therefore not a private experience,
not a bare function, and not a machine-learning model by itself. A
lawlike claim is a stable, classifier-respecting, failure-exposed
certificate over finite observation-time traces.

The same structure explains why scientific inquiry repeatedly encounters
$\mathsf{T}$-supply sockets. Finite observation records can support finite
fit internally. They cannot, by themselves, generate unrestricted future
truth, universal induction, or final explanation. When a theory projects
beyond its finite source horizon, BEDC does not hide that projection as
an axiom. It records the socket, the requested supply kind, the audit
gate, and the failure surface.
\end{remark}

\begin{remark}[Closure obligations]
\label{rem:scientific-inquiry-conscious-t-closure-obligations}
Closing this vision-seed horizon would require a classifier linking
focused $\mathsf{ConsciousRecord}$ source traces to public scientific
source rows; $\hsame$-stable and inter-$\Hist$-stable transport for
replicated scientific observations; fit classifiers between observed and
model-generated signatures; stability and descent obligations for every
predictive or explanatory reuse; failure surfaces for lawlike appearance;
$\mathsf{T}$-socket rows for future-binding claims not generated by
current finite records; and audit gates refusing subject-substance,
global-clock, hidden-choice, unledgered-compression, and object-level
$\mathsf{T}$ promotions.
\end{remark}

\concretizedIn{ch:concrete-instances-scientificmodelbridge-namecert}{Scientific model bridges supply the public model, signature, classifier, stability, descent, ledger, failure-surface, and audit-strength discipline consumed by this schema.}
\concretizedIn{ch:concrete-instances-focused-ledger-namecert}{Focused ledgers supply the records-side carrier for focused Hist-time readback without adding subject-substance.}
\concretizedIn{ch:concrete-instances-observerhistidentity-namecert}{Observer-Hist identity supplies observer as $\Hist$ and observation as local continuation without adding a global observer.}
\concretizedIn{ch:concrete-instances-supplysocketledger-namecert}{Supply socket ledgers record future-binding requests as finite socket rows rather than hidden axioms or model components.}
