\section{Scientific Inquiry as Ledgered Reflection of Hist-Time}
\label{sec:scientific-inquiry-ledgered-reflection-hist-time}
\origin{ai}

\begin{remark}[Vision seed status]
\label{rem:scientific-inquiry-hist-time-vision-seed-status}
This interface has vision-seed status: it is a schema horizon and has no
Lean target. It is not a finite-kernel theorem. It records the certificate
shape a later development would have to close before scientific inquiry,
lawlike fit, or model-mediated prediction could be reported as a BEDC
theorem about reality.

The schema uses only the current BEDC reading that observer identity is
internal to $\Hist$, that $\Cont$ has only history-valued arguments, and
that observation, distinction, and local time-step share the same
continuation form. It does not assert a primitive equation
$$
\mathsf{Science}=\mathsf{Time}.
$$
Kernel time is $\Hist$ growth by $\Eone/\Ezero$ distinctions. Scientific
inquiry is a derived, ledgered, classifier-governed reflection on such
local Hist-time. It treats the traces left by observation-time as sources,
extracts signatures from them, compares observed and model-generated
signatures by licensed classifiers, and records the stability, descent,
provenance, and failure surfaces required before a pattern may be reused
as lawlike.
\end{remark}

\begin{definition}[Scientific inquiry context]
\label{def:scientific-inquiry-context}
A \emph{scientific inquiry context} is a ledger-readable package
$$
S=(h,\Pi,X,\mathsf{Obs},M,\mathsf{Mod},C,D,L,\Phi),
$$
where $h:\Hist$ is the observer-history, $\Pi$ is a repeated probe
pattern or probe bundle, $X$ is a candidate phenomenon or observed
interface, $\mathsf{Obs}$ is the finite family of observed signatures
generated by applying $\Pi$ inside $h$, $M$ is a candidate model family,
$\mathsf{Mod}$ is the finite family of model-generated signatures exposed
for comparison with $\mathsf{Obs}$, $C$ is the classifier of fit between
observed and model-generated signatures, $D$ records the announced
stability and descent obligations, $L$ records source, pattern,
classifier, stability, and hidden-provenance data, and $\Phi$ is the
failure surface specifying which future observations would defeat or
downgrade the present claim.
\end{definition}

\begin{definition}[Scientific reflection prefix]
\label{def:scientific-reflection-prefix}
For a scientific inquiry context $S$, a \emph{scientific reflection
prefix} of length $N$ is a finite sequence
$$
Q^{S}_{N}=(q_{0},q_{1},\ldots,q_{N})
$$
whose entries are BEDC-visible query, response, signature, classifier,
and ledger rows generated by repeatedly applying $\Pi$ to $X$ as recorded
in $h$. An infinite scientific stream is admissible here only as a schema
whose every finite prefix is ledger-visible; no completed external stream
and no global science-time are added to the kernel.
\end{definition}

\begin{definition}[Time-reflective fit]
\label{def:time-reflective-fit}
A scientific reflection prefix $Q^{S}_{N}$ has \emph{time-reflective fit}
when the ledger supplies:
\begin{enumerate}
\item source generation witnesses showing that the observed signatures
arise from finite $\Cont$ traces in $h$;
\item model-generation witnesses exposing the corresponding signatures of
$M$;
\item classifier witnesses $C$ relating the observed and model-generated
signatures;
\item $\hsame$-stability and descent witnesses showing that the comparison
respects the announced source and target classifiers;
\item ledger rows recording any compression, idealization, hidden
provenance, or approximation used by the comparison.
\end{enumerate}
\end{definition}

\begin{definition}[Lawlike and speculative appearance]
\label{def:lawlike-speculative-appearance}
A scientific reflection prefix $Q^{S}_{N}$ has \emph{lawlike appearance}
relative to $S$ when it has time-reflective fit and the ledger also
supplies stability over the announced continuation class $D$ together
with an explicit failure surface $\Phi$. It has \emph{speculative
appearance} relative to $S$ when a finite fit is present but at least one
of stability, descent, ledger completeness, or failure-surface exposure
remains open.

The phrase lawlike appearance is part of the schema. It does not assert
that the model is identical with reality, that a function is identical
with a law, or that scientific inquiry is identical with time itself. It
classifies observer-relative, certificate-governed reuse of finite
observation-time traces.
\end{definition}

\begin{proposition}[Science is not time itself]
\label{prop:science-not-time-itself}
Within a fixed scientific inquiry context, scientific inquiry is not
kernel time itself. It is ledgered reflection on local Hist-time.
\end{proposition}

\begin{proof}
Kernel time is generated by a single $\Eone/\Ezero$ distinction step and
by finite $\Cont$ growth of $\Hist$. A scientific inquiry context requires
additional fields: a probe bundle, observed signatures, model-generated
signatures, a fit classifier, stability and descent obligations, a
provenance ledger, and a failure surface. These fields are not produced
by every $\Cont$ step. Hence $\Hist$ growth implies local time, but does
not by itself imply scientific inquiry.

Conversely, without local Hist-time there are no generated observation
traces from which source signatures can be extracted. Scientific inquiry
therefore depends on Hist-time as its source material, but it is not
identical with Hist-time. It is the certificate-governed reuse and
reflection of traces generated in time.
\end{proof}

\begin{corollary}[No context-free science-time predicate]
\label{cor:no-context-free-science-time-predicate}
The schema licenses only context-indexed judgments such as
$\mathsf{ScientificFit}^{S}_{N}(Q)$, $\mathsf{Lawlike}^{S}_{N}(Q)$, and
$\mathsf{Speculative}^{S}_{N}(Q)$. It does not license an unindexed
kernel predicate $\mathsf{Science}=\mathsf{Time}$ or
$\mathsf{Science}(\mathsf{Time})$ as a completed global object.
\end{corollary}

\begin{proof}
Removing the context $S$ removes the observer-history, probe pattern,
target interface, observed signatures, model signatures, classifier,
stability and descent obligations, ledger, and failure surface. BEDC
supplies no global observer, no global clock, no context-free classifier,
and no external equality oracle capable of replacing these fields.
\end{proof}

\begin{remark}[Reading]
\label{rem:scientific-inquiry-hist-time-reading}
Scientific inquiry is local time becoming ledger-readable to itself. The
observation-distinction-time identity supplies the raw form of trace
generation; scientific method adds signature extraction, classifier
comparison, model reuse, stability, descent, ledger exposure, and failure
conditions. The safe compressed reading is therefore not
$$
\mathsf{Science}=\mathsf{Time},
$$
but
$$
\mathsf{Science}
=
\mathsf{LedgeredReflection}(\mathsf{HistTime}).
$$
Under this reading, a scientific law is not a bare function and a
machine-learning model is not a law. A lawlike claim is a stable,
classifier-respecting, failure-exposed certificate over finite
observation-time traces. A model, including a computational or learning
model, is a candidate generator of signatures whose scientific status
depends on the audit fields above.
\end{remark}

\concretizedIn{ch:concrete-instances-scientificmodelbridge-namecert}{Scientific model bridges realize this vision as finite scientific-object, model-audit, standard-bridge-audit, open-fit, failure-surface, transport, provenance, and NameCert rows.}
\concretizedIn{ch:concrete-instances-reality-constrained-model-audit-namecert}{Reality-constrained model audits realize the source-trace, observed-signature, model-signature, classifier, tower, stability, descent, ledger, failure-surface, and audit-strength rows required by the schema.}
\concretizedIn{ch:concrete-instances-observerhistidentity-namecert}{Observer-Hist identity supplies observer as $\Hist$ without adding observer-substance.}
\concretizedIn{ch:concrete-instances-histtimestream-namecert}{Hist time streams supply finite local $\Cont$-step rows without adding a global clock.}
