\chapter{A Concrete Naming Certificate for $\MetaCICDiamondResidualBudgetUp$}
\label{ch:concrete-instances-metacic-diamond-residual-budget-namecert}
\origin{ai}

The $\MetaCICDiamondResidualBudgetUp$ packet realizes the finite residual-budget boundary of \autoref{ch:metacic-confluence-audit-map}. It sits beside the local diamond witness of \autoref{ch:concrete-instances-metacic-local-diamond-witness-namecert}, the residual envelope of \autoref{ch:concrete-instances-metacic-confluence-residual-envelope-namecert}, the substitution boundary of \autoref{ch:concrete-instances-metacic-confluence-substitution-boundary-namecert}, and the closed parallel diamond premise ledger of \autoref{ch:concrete-instances-closed-parallel-diamond-premise-ledger-namecert}. The packet names the finite rows still required by the conditional confluence route without claiming the full parallel diamond theorem.

\begin{definition}[MetaCIC diamond residual budget carrier]
\label{def:metacic-diamond-residual-budget-carrier}
A $\MetaCICDiamondResidualBudgetUp$ carrier is a finite $\BHist$ packet
$$
B=(T,F,R,J,S,E,L,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the typed-window row for the source and target terms whose residual branches are audited.
\item $F$ is the redex-frontier row that lists the beta redexes and congruence faces inspected by the local diamond route.
\item $R$ is the residual-budget row, recording the finite fuel and residual-address accounting needed to replay candidate joins.
\item $J$ is the candidate-join row, naming the displayed joins produced from $F$ and $R$.
\item $S$ is the substitution-boundary row, keeping the residual-substitution compatibility premise visible.
\item $E$ is the residual-envelope row, read through \autoref{ch:concrete-instances-metacic-confluence-residual-envelope-namecert}.
\item $L$ is the closed parallel diamond premise ledger row, read through \autoref{ch:concrete-instances-closed-parallel-diamond-premise-ledger-namecert}.
\item $D$ is the local diamond witness row, read through \autoref{ch:concrete-instances-metacic-local-diamond-witness-namecert} as finite local geometry rather than a proof of the closed endpoint.
\item $H$ records componentwise $\hsame$ transport for typed windows, frontier rows, residual budgets, candidate joins, substitution boundary, residual envelope, premise ledger, local diamond witness, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
T,F,R,S \longmapsto J \longmapsto E,L,D \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\MetaCICDiamondResidualBudgetUp$, MetaCIC beta reduction, $\mathsf{BetaParallel}$, $\mathsf{BetaStarStep}$, the named sibling packets, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetaCICDiamondResidualBudgetUp}$ row.
\end{enumerate}
The carrier has no coordinate proving $\mathsf{BetaParallelSubstitutionCompatibility}$, no coordinate proving full parallel diamond, no coordinate proving arbitrary closed Church--Rosser, and no host substitution semantics.
\end{definition}

\begin{theorem}[MetaCIC diamond residual budget NameCert obligations]
\label{thm:metacic-diamond-residual-budget-namecert-obligations}
For every accepted $\MetaCICDiamondResidualBudgetUp$ carrier $B=(T,F,R,J,S,E,L,D,H,C,P,N)$, the local $\NameCert_{\MetaCICDiamondResidualBudgetUp}$ surface consists exactly of typed-window admission through $T$, redex-frontier exposure through $F$, residual-budget accounting through $R$, candidate-join display through $J$, substitution-boundary visibility through $S$, residual-envelope handoff through $E$, closed-premise-ledger handoff through $L$, local-diamond witness handoff through $D$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-diamond-residual-budget-carrier}. The displayed rows are exactly $T,F,R,J,S,E,L,D,H,C,P,N$, so carrier admission is a finite projection.

The residual budget is read before any candidate join is exported. Rows $T$ and $F$ name the typed window and redex frontier, while $R$ records the finite residual-address and fuel accounting required by the join row $J$.

The substitution row $S$ remains visible downstream. The residual envelope $E$, premise ledger $L$, and local diamond witness $D$ are sibling handoffs, not discharges of $S$ or proofs of the full diamond endpoint.

Finally $H,C,P,N$ transport, replay, source, and name the same rows. With no coordinate for the refused endpoint claims, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[MetaCIC diamond residual budget endpoint boundary]
\label{thm:metacic-diamond-residual-budget-endpoint-boundary}
Any confluence consumer of an accepted $\MetaCICDiamondResidualBudgetUp$ packet may cite only the displayed residual-budget route
$$
T,F,R,S \longmapsto J \longmapsto E,L,D \longmapsto H,P,N .
$$
It may not promote the candidate-join row or residual-envelope row into $\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or arbitrary closed Church--Rosser.
\end{theorem}
\begin{proof}
Start with the displayed route. The carrier gives the consumer typed windows, redex-frontier data, residual-budget accounting, a substitution-boundary row, candidate joins, the residual envelope, the closed-premise ledger, and the local diamond witness.

Use \autoref{thm:metacic-diamond-residual-budget-namecert-obligations}. Its substitution-boundary visibility keeps $S$ attached whenever $J$ is exported, and its sibling rows keep $E,L,D$ as contextual handoffs rather than endpoint proofs.

Transport, replay, provenance, and local naming preserve the same finite route. Therefore the packet can expose residual-budget coverage and candidate joins, but it cannot supply a premise-free parallel diamond theorem or arbitrary closed Church--Rosser theorem.
\end{proof}

\begin{theorem}[MetaCIC diamond residual budget fuel monotonicity]
\label{thm:metacic-diamond-residual-budget-fuel-monotonicity}
Suppose an accepted $\MetaCICDiamondResidualBudgetUp$ packet is extended only by
enlarging the finite residual-budget row $R$, while preserving the typed window
$T$, redex frontier $F$, substitution boundary $S$, candidate join row $J$,
residual envelope $E$, premise ledger $L$, local diamond row $D$, transport
$H$, replay $C$, provenance $P$, and local naming $N$. Then every confluence
consumer remains on the same endpoint-boundary route
$$
T,F,R,S \longmapsto J \longmapsto E,L,D \longmapsto H,P,N ,
$$
and the extended packet still cannot infer
$\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or
arbitrary closed Church--Rosser.
\end{theorem}
\begin{proof}
Project the accepted carrier of
\autoref{def:metacic-diamond-residual-budget-carrier}. The only coordinate
changed by the comparison is the finite residual-budget row $R$; all other
displayed rows are preserved.

The candidate join row $J$ remains attached to the same typed window, redex
frontier, and visible substitution boundary. Enlarging $R$ supplies more
displayed fuel for the same finite accounting route, but it does not add a new
endpoint row.

Apply
\autoref{thm:metacic-diamond-residual-budget-endpoint-boundary}. The consumer
therefore still reads through $T,F,R,S,J,E,L,D,H,P,N$ and cannot promote the
budget extension into the refused endpoint claims.
\end{proof}

\begin{theorem}[MetaCIC residual-budget frontier accounting]
\label{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}
For every accepted $\MetaCICDiamondResidualBudgetUp$ carrier
$B=(T,F,R,J,S,E,L,D,H,C,P,N)$, the typed-window row $T$, redex-frontier row
$F$, residual-budget row $R$, and substitution-boundary row $S$ must be
displayed before $J$ is a valid candidate-join row. A consumer that reads $J$
without the prior $T,F,R,S$ accounting is outside the accepted residual-budget
carrier.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:metacic-diamond-residual-budget-carrier}. The candidate-join
coordinate $J$ is not a primitive endpoint theorem; it is listed after typed
windows, redex frontiers, residual budgets, and the visible substitution
boundary.

Apply
\autoref{thm:metacic-diamond-residual-budget-endpoint-boundary}. The displayed
route places $T,F,R,S$ before $J$, and the endpoint boundary prevents the join
row from being read as a premise-free confluence theorem.

Thus $J$ is valid only as a candidate-join row mediated by the frontier and
budget accounting rows already displayed in the carrier.
\end{proof}

\begin{theorem}[MetaCIC residual-budget substitution visibility]
\label{thm:metacic-diamond-residual-budget-substitution-visibility}
Every accepted candidate-join read through $J$ keeps the substitution-boundary row $S$ visible along the route
$$
T,F,R,S \longmapsto J \longmapsto E,L,D \longmapsto H,P,N .
$$
Therefore a residual-budget read cannot be promoted to $\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or arbitrary closed Church--Rosser.
\end{theorem}
\begin{proof}
Use \autoref{thm:metacic-diamond-residual-budget-endpoint-boundary}. Its displayed route places typed windows $T$, redex frontiers $F$, residual budgets $R$, and the substitution boundary $S$ before any candidate join $J$ is exported.

Apply \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}. It states that a $J$ read without prior $T,F,R,S$ accounting lies outside the accepted residual-budget carrier.

The downstream rows $E,L,D,H,P,N$ are sibling handoffs and structural rows on the same route. They do not discharge $S$ or add an endpoint proof, so the accepted read remains a finite residual-budget boundary rather than a promoted confluence theorem.
\end{proof}

\begin{theorem}[MetaCIC residual-budget substitution preservation]
\label{thm:metacic-diamond-residual-budget-substitution-preservation}
Suppose an accepted $\MetaCICDiamondResidualBudgetUp$ packet is extended only in the residual-budget row $R$, while preserving the typed window $T$, redex frontier $F$, substitution boundary $S$, candidate joins $J$, residual envelope $E$, premise ledger $L$, local diamond row $D$, and structural rows $H,C,P,N$. Then every accepted candidate-join read still keeps $S$ visible along the route
$$
T,F,R,S \longmapsto J \longmapsto E,L,D \longmapsto H,P,N .
$$
The preservation claim does not assert $\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or closed Church--Rosser.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-diamond-residual-budget-carrier}. The comparison changes only the residual-budget coordinate $R$; the typed window, redex frontier, substitution boundary, candidate joins, sibling handoffs, and structural rows are preserved.

Use \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}. A candidate-join read remains accepted only when $T,F,R,S$ are displayed before $J$, so extending $R$ cannot detach $J$ from the visible substitution boundary.

Apply \autoref{thm:metacic-diamond-residual-budget-substitution-visibility}. The substitution row $S$ remains visible through every accepted candidate-join read, and \autoref{thm:metacic-diamond-residual-budget-endpoint-boundary} keeps the downstream route confined to $E,L,D,H,P,N$.

Thus the preserved rows carry the same visible substitution boundary under a larger residual budget. The packet still lacks any endpoint coordinate for $\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or closed Church--Rosser.
\end{proof}

\begin{theorem}[MetaCIC residual-budget candidate-join visibility]
\label{thm:metacic-diamond-residual-budget-obligation-candidate-join-visibility}
Every consumer of the candidate-join row $J$ in an accepted
$\MetaCICDiamondResidualBudgetUp$ packet must also expose the residual-envelope
handoff $E$, closed-premise-ledger handoff $L$, local-diamond handoff $D$, and
the structural rows $H,C,P,N$. The candidate join is therefore consumed only
through the displayed sibling handoffs and local NameCert structure.
\end{theorem}
\begin{proof}
Project the same carrier. The rows following $J$ are precisely the sibling
handoffs $E,L,D$ and the structural rows $H,C,P,N$.

Use \autoref{thm:metacic-diamond-residual-budget-endpoint-boundary}. Its route
continues from $J$ through $E,L,D$ and then through the transport, replay,
provenance, and naming rows.

Therefore a consumer of $J$ must keep the residual envelope, closed premise
ledger, local diamond witness, and local structural surface visible. Nothing
in the carrier permits a bare candidate-join read detached from those rows.
\end{proof}

\begin{theorem}[MetaCIC residual-budget endpoint non-escape]
\label{thm:metacic-diamond-residual-budget-obligation-endpoint-nonescape}
No accepted $\MetaCICDiamondResidualBudgetUp$ packet proves
$\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or
arbitrary closed Church--Rosser. The packet exposes only typed windows, redex
frontiers, residual budgets, candidate joins, substitution-boundary visibility,
sibling handoffs, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:metacic-diamond-residual-budget-carrier}. Its coordinates are
$T,F,R,J,S,E,L,D,H,C,P,N$, and none of them is an endpoint proof row for
substitution compatibility, full parallel diamond, or closed Church--Rosser.

Apply
\autoref{thm:metacic-diamond-residual-budget-endpoint-boundary}. The endpoint
boundary states that confluence consumers remain on the displayed
residual-budget route and may not promote candidate joins or residual
envelopes into the refused endpoint claims.

Transport, replay, provenance, and naming preserve the same finite packet.
They do not add endpoint proof data, so the three endpoint claims remain
outside the accepted certificate.
\end{proof}

\begin{theorem}[MetaCIC residual-budget local join]
\label{thm:metacic-diamond-residual-budget-local-join}
If an accepted $\MetaCICDiamondResidualBudgetUp$ packet exposes typed window $T$, redex frontier $F$, residual budget $R$, substitution row $S$, candidate join $J$, residual envelope $E$, premise ledger $L$, and local diamond row $D$, then any local join consumed through $J$ is valid only under the displayed residual fuel and visible substitution boundary. The packet cannot be read as $\mathsf{BetaParallelSubstitutionCompatibility}$, full parallel diamond, or full Church--Rosser.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-diamond-residual-budget-carrier}. The candidate join row $J$ is displayed only after the typed window $T$, redex frontier $F$, residual budget $R$, and substitution-boundary row $S$.

Apply \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}. It keeps the redex-frontier accounting and residual fuel visible before $J$ can be read by a confluence-facing consumer.

Apply \autoref{thm:metacic-diamond-residual-budget-substitution-visibility}. It keeps $S$ attached along the route from $T,F,R,S$ through $J$, so the join is not a substitution-compatibility theorem detached from its boundary.

Finally use \autoref{thm:metacic-diamond-residual-budget-obligation-endpoint-nonescape}. The residual envelope $E$, premise ledger $L$, and local diamond row $D$ remain sibling handoffs for a bounded candidate route, not endpoint proofs of BetaParallelSubstitutionCompatibility, full parallel diamond, or Church--Rosser.
\end{proof}

\begin{theorem}[MetaCIC residual-budget candidate-mediated SN handoff]
\label{thm:metacic-diamond-residual-budget-candidate-sn-handoff}
Every accepted $\MetaCICDiamondResidualBudgetUp$ packet consumed by a bounded candidate-mediated strong-normalization reader must expose typed window $T$, redex frontier $F$, residual budget $R$, substitution boundary $S$, candidate join $J$, residual envelope $E$, premise ledger $L$, local diamond row $D$, and structural rows $H,C,P,N$ before the SN reader may consume the candidate route. The packet does not assert global strong normalization, global confluence, or substitution compatibility.
\end{theorem}
\begin{proof}
Begin with the frontier accounting theorem, \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}. It requires $T,F,R,S$ to be displayed before $J$ is a valid candidate-join row, so a candidate-mediated SN reader cannot consume $J$ as a free-standing normalization witness.

Apply substitution visibility, \autoref{thm:metacic-diamond-residual-budget-substitution-visibility}. The substitution boundary $S$ remains attached along the route from the typed window and frontier rows through the candidate join, so the handoff is not a proof of substitution compatibility.

Use the local-join theorem, \autoref{thm:metacic-diamond-residual-budget-local-join}. It keeps every local join under the displayed residual fuel and visible substitution boundary while routing the consumer through the residual envelope $E$, premise ledger $L$, and local diamond row $D$.

Finally apply endpoint non-escape, \autoref{thm:metacic-diamond-residual-budget-obligation-endpoint-nonescape}. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite route, and no carrier coordinate supplies global strong normalization, global confluence, or $\mathsf{BetaParallelSubstitutionCompatibility}$.
\end{proof}

\begin{theorem}[MetaCIC residual-budget candidate-window exhaustion]
\label{thm:metacic-diamond-residual-budget-candidate-window-exhaustion}
Every candidate-mediated strong-normalization consumer of an accepted $\MetaCICDiamondResidualBudgetUp$ packet must exhaust the displayed finite typed window $T$, redex frontier $F$, residual budget $R$, and substitution boundary $S$ before reading the candidate join $J$. The consumer must then keep the residual envelope $E$, premise ledger $L$, local diamond row $D$, and structural rows $H,C,P,N$ attached to that same finite route. This exhaustion theorem does not infer global strong normalization, substitution compatibility, full parallel diamond, or Church--Rosser.
\end{theorem}
\begin{proof}
Begin with frontier accounting, \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}. It makes the typed window, redex frontier, and residual budget visible before any candidate join can be consumed.

Next use substitution visibility, \autoref{thm:metacic-diamond-residual-budget-substitution-visibility}. The boundary row $S$ remains attached to the candidate route, so exhaustion cannot be replaced by a global substitution-compatibility claim.

Apply the local-join theorem, \autoref{thm:metacic-diamond-residual-budget-local-join}. It keeps the candidate join $J$ under the displayed residual fuel and routes the consumer through $E,L,D$ rather than through a full parallel diamond theorem.

Finally use endpoint non-escape, \autoref{thm:metacic-diamond-residual-budget-obligation-endpoint-nonescape}, together with \autoref{thm:metacic-diamond-residual-budget-candidate-sn-handoff}. The structural rows $H,C,P,N$ preserve and name the same finite route, so the SN consumer exhausts the candidate window without obtaining global strong normalization, Church--Rosser, or unbounded confluence.
\end{proof}

\begin{theorem}[MetaCIC residual-budget premise alignment]
\label{thm:metacic-diamond-residual-budget-premise-alignment}
Every accepted $\MetaCICDiamondResidualBudgetUp$ packet consumed by a candidate-mediated strong-normalization reader must expose the residual envelope $E$, closed premise ledger $L$, and local diamond row $D$ together, after typed window $T$, redex frontier $F$, residual budget $R$, substitution boundary $S$, and candidate join $J$, and before the structural rows $H,C,P,N$. Dropping any one of $E,L,D$ leaves only a frontier packet, not a valid confluence-facing residual-budget premise.
\end{theorem}
\begin{proof}
Start with candidate-join visibility, \autoref{thm:metacic-diamond-residual-budget-obligation-candidate-join-visibility}. It places the accepted candidate route after the typed window, redex frontier, residual budget, and substitution boundary, so a consumer cannot read $J$ before the displayed frontier rows.

Next apply the local-join theorem, \autoref{thm:metacic-diamond-residual-budget-local-join}. The local join remains under the residual fuel and visible substitution boundary while routing through the residual envelope $E$, premise ledger $L$, and local diamond row $D$.

Finally use the candidate-mediated SN handoff, \autoref{thm:metacic-diamond-residual-budget-candidate-sn-handoff}. It requires $E,L,D$ before the structural transport, replay, provenance, and naming rows are consumed by the SN reader. If any one of $E,L,D$ is absent, the reader has only the frontier and candidate route, so the packet has not yet supplied the confluence-facing residual-budget premise.
\end{proof}

\falsifiablePrediction{A confluence packet that omits either the residual-budget row $R$ or the candidate-join row $J$ is rejected as a $\MetaCICDiamondResidualBudgetUp$ packet, even when it carries local diamond, residual-envelope, or closed-premise-ledger rows.}

\independenceWitness{metacic-local-diamond-witness, metacic-confluence-residual-envelope, metacic-confluence-substitution-boundary, closed-parallel-diamond-premise-ledger: $\MetaCICDiamondResidualBudgetUp$ is not bijective to any listed sibling because it binds typed windows, redex frontiers, residual-budget accounting, candidate joins, a visible substitution boundary, residual envelope, premise ledger, local diamond witness, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ into one finite confluence-facing packet.}

The Lean-side hardening surface requires $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for the residual-budget packet. The nontrivial witness separates a carrier with displayed residual-budget and candidate-join rows from a refused packet missing one of those rows; field faithfulness matches on $T,F,R,J,S,E,L,D,H,C,P,N$ so two accepted packets with the same displayed fields are indistinguishable to the NameCert classifier.

\closureat{MetaCICDiamondResidualBudgetUp}{obligationStr}

\begin{closurestatus}{\MetaCICDiamondResidualBudgetUp}
  \constructivestory{A $\MetaCICDiamondResidualBudgetUp$ packet is generated from typed windows, redex frontiers, residual-budget accounting, candidate joins, a visible substitution-boundary row, residual-envelope and closed-premise-ledger handoffs, a local diamond witness, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:metacic-diamond-residual-budget-carrier}, \autoref{thm:metacic-diamond-residual-budget-namecert-obligations}, \autoref{thm:metacic-diamond-residual-budget-obligation-frontier-accounting}, and \autoref{thm:metacic-diamond-residual-budget-obligation-endpoint-nonescape} close the finite residual-budget obligation surface for the MetaCIC confluence route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close BetaParallelSubstitutionCompatibility, full parallel diamond, arbitrary closed Church--Rosser, host substitution semantics, Lean verification, or bridge checking.}
  \upgradepath{Lean verification requires checked typed-window admission, redex-frontier exposure, residual-budget accounting, candidate-join display, substitution-boundary visibility, sibling handoffs, endpoint nonescape, and TasteGate nontriviality with field faithfulness for BEDC.Derived.MetaCICDiamondResidualBudgetUp.}
\end{closurestatus}
