\begin{theorem}[RegularCauchyFiniteProduct coordinate stability]
\label{thm:regular-cauchy-finite-product-coordinate-stability}
If two accepted $\RegularCauchyFiniteProductUp$ packets are classifier-equivalent, then each projected coordinate remains a $\RegSeqRatUp$-compatible regular Cauchy readback under the same $\StreamNameUp$ windows and product-projection rows. In particular, a coordinate projection cannot separate the two packets unless the separation is already visible in the finite product source row, synchronized window family, dyadic product-budget ledger, regular-rational readback, or displayed projection route.
\end{theorem}
\begin{proof}
Read the product projection route first. The dependency route through \autoref{ch:concrete-instances-regular-cauchy-product-projection-namecert} exposes the finite product source, synchronized windows, dyadic product budget, and projection readback as the only public route to a coordinate.

Next read the regular-rational and stream-name route. The dependency line through \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-streamname-namecert} fixes the windows and readback rows used by each coordinate.

Classifier equivalence of the two finite-product packets therefore transports through the same source, window, budget, readback, and projection rows. Each coordinate remains a RegSeqRat-compatible regular Cauchy readback, and any failure of stability must already be visible in one of the displayed rows rather than in a hidden host product or selected component representative.
\end{proof}
