\chapter{A Concrete Naming Certificate for $\RegularCauchyFiniteProductUp$}
\label{ch:concrete-instances-regular-cauchy-finite-product-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy real arithmetic, the $\RegularCauchyFiniteProductUp$ packet records the finite product of displayed regular Cauchy rational names as one synchronized NameCert route. It sits after the regular rational source surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the binary regular product route of \autoref{ch:concrete-instances-regularcauchyproduct-namecert}, and the completion-facing product packet of \autoref{ch:concrete-instances-cauchyproduct-namecert}. The carrier packages repeated binary product evidence without importing a host finite product, quotient stream equality, selected limits, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy finite product carrier]\label{def:regular-cauchy-finite-product-carrier}
A $\RegularCauchyFiniteProductUp$ carrier is a finite $\BHist$ packet
$$
K=(I,S,W,D,P,R,E,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite unary index row. It lists exactly the component slots opened by the product request and the fold order used by the displayed route.
\item $S$ is the component $\RegSeqRatUp$ source family, one row for each slot of $I$.
\item $W$ is the synchronized $\StreamNameUp$ window family for the component reads, intermediate product reads, and final product-facing read.
\item $D$ is the $\DyadicRatCoreUp$ observation row, storing the component dyadic observations, intermediate product observations, requested radii, and slack cells.
\item $P$ is the finite product-budget ledger. It records the binary-product schedule, radius allocation, and accumulated dyadic error account for the fold named by $I$.
\item $R$ is the $\RegSeqRatUp$ readback row for the final folded product, obtained only from $S,W,D,P$.
\item $E$ is the $\RealUp$ seal row reached after the regular readback of the folded product has been displayed.
\item $H$ records componentwise $\hsame$ transport for the index row, sources, synchronized windows, dyadic observations, product-budget ledger, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any finite product request through the same rows.
\item $Q$ is the $\Pkg$ provenance over $\RegularCauchyFiniteProductUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyProductUp$, $\CauchyProductUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyFiniteProductUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,S,W,D,P,R,E,H,C,Q,N$. It has no coordinate for a host finite product, quotient stream equality, selected limit, trichotomy, ambient $\RealUp$ completeness, Lean verification, or standard bridge.
\end{definition}

\begin{theorem}[Regular Cauchy finite product NameCert obligations]\label{thm:regular-cauchy-finite-product-namecert-obligations}
For every accepted $\RegularCauchyFiniteProductUp$ carrier
$$
K=(I,S,W,D,P,R,E,H,C,Q,N),
$$
the local $\NameCert_{\RegularCauchyFiniteProductUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission for the finite unary index row, component $\RegSeqRatUp$ sources, synchronized $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observations, product-budget ledger, final readback, $\RealUp$ seal, transport, replay, provenance, and local name;
\item finite tuple-window coverage, requiring every component slot in $I$ to open the matching source row and all synchronized windows needed by the fold;
\item dyadic product-budget exactness, requiring every intermediate product observation to consume its assigned radius and slack cells from $D$ and $P$;
\item RegSeqRat readback stability, requiring the final readback row $R$ to depend only on the displayed sources, windows, dyadic observations, and product-budget ledger;
\item Real seal non-escape, requiring $E,H,C,Q,N$ to expose no host finite product, quotient stream equality, selected limit, trichotomy, ambient completeness theorem, Lean verification, or bridge credential.
\end{enumerate}
No Regular Cauchy finite product obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:regular-cauchy-finite-product-carrier}. The displayed tuple $I,S,W,D,P,R,E,H,C,Q,N$ is the entire public surface, so carrier admission is exactly the admission of those rows.

Tuple-window coverage is forced by the index row. Each slot named by $I$ has one component $\RegSeqRatUp$ source in $S$, and the synchronized window row $W$ is the only place where component, intermediate, and final product reads are opened.

Dyadic exactness is the joint role of $D$ and $P$. The observations in $D$ supply component and intermediate dyadic cells, while $P$ assigns the binary-product schedule, radii, slack, and accumulated error account for the fold.

The final regular readback row $R$ is downstream of $S,W,D,P$. Therefore readback stability follows from the carrier order: no product-facing $\RegSeqRatUp$ data can be inspected until the synchronized windows and dyadic product budget have already been displayed.

Finally, the seal, transport, replay, provenance, and local name rows preserve only this displayed route. Since none of the excluded objects is a coordinate of the carrier, the listed five rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Regular Cauchy finite product tail budget]\label{thm:regular-cauchy-finite-product-tail-budget}
Let
$$
K=(I,S,W,D,P,R,E,H,C,Q,N)
$$
be an accepted $\RegularCauchyFiniteProductUp$ carrier. Every finite product read from $K$ factors through
$$
I,S \longmapsto W \longmapsto D,P \longmapsto R \longmapsto E,H,C,Q,N .
$$
In particular, no read reaches the final $\RegSeqRatUp$ product row before the synchronized windows and dyadic product-budget ledger have been displayed.
\end{theorem}
\begin{proof}
Begin with a finite product request. The request first names its finite unary index row $I$ and the component source family $S$, because those are the only carrier rows that identify which regular Cauchy names participate in the fold.

The requested component and intermediate observations then pass through $W$. This synchronized window row is the only row that aligns the component reads with the intermediate product reads used by the fold.

The dyadic part of the request is read next. The observation row $D$ supplies the dyadic product cells and requested radii, while the budget row $P$ supplies the binary-product schedule and accumulated slack account.

Only after those rows are displayed can the final regular rational readback $R$ be consumed. The downstream rows $E,H,C,Q,N$ seal, transport, replay, source, and name the same route, so the finite product read cannot bypass the synchronized windows or the dyadic ledger.
\end{proof}

\begin{theorem}[Regular Cauchy finite product budget associativity]\label{thm:regular-cauchy-finite-product-budget-associativity}
Let
$$
K=(I,S,W,D,P,R,E,H,C,Q,N)
$$
be an accepted $\RegularCauchyFiniteProductUp$ carrier. Regrouping adjacent binary product folds in the displayed fold order preserves the same synchronized windows $W$, dyadic observations $D$, product-budget ledger $P$, final $\RegSeqRatUp$ readback $R$, and $\RealUp$ seal $E$. The regrouped read is a projection of the displayed fold rows of $K$, not an appeal to host associativity of finite products or quotient stream equality.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regular-cauchy-finite-product-tail-budget}. Every finite product read from $K$ factors through the index and source rows, then through the synchronized windows, then through the dyadic observations and product-budget ledger, before reaching the final readback and seal.

The carrier rows of \autoref{def:regular-cauchy-finite-product-carrier} identify where regrouping can be displayed. The finite unary index row $I$ names the fold order, while $W,D,P$ record the windows, observations, product schedule, radii, and slack cells used by that order.

Regrouping adjacent binary product folds therefore changes only the displayed parenthesization inside the schedule already stored in $I$ and $P$. It does not create a second window family, a second dyadic observation row, a second product-budget ledger, or a second final readback.

Since $R$ and $E$ are downstream of the fixed rows $W,D,P$, the regrouped read preserves the same final $\RegSeqRatUp$ readback and $\RealUp$ seal. The argument is projection from the accepted carrier, so no host finite-product operation or quotient stream equality is introduced.
\end{proof}

\begin{theorem}[Regular Cauchy finite product projection stability]\label{thm:regular-cauchy-finite-product-projection-stability}
For every accepted $\RegularCauchyFiniteProductUp$ carrier $K=(I,S,W,D,P,R,E,H,C,Q,N)$, projecting any component slot from $K$ factors through the same finite index row $I$, source family $S$, synchronized $\StreamNameUp$ window family $W$, dyadic product-budget ledger $D,P$, final $\RegSeqRatUp$ readback $R$, and $\RealUp$ seal $E$. Component projection can expose a component readback only through this displayed route; it cannot bypass the budget ledger or invoke host finite products, quotient stream equality, selected component representatives, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:regular-cauchy-finite-product-carrier}. The component slot is named by $I$, its source is a row of $S$, and every read serving the projection must pass through the synchronized window family $W$.

Apply the tail-budget theorem \autoref{thm:regular-cauchy-finite-product-tail-budget}. It places every product-facing read through $I,S,W,D,P,R,E,H,C,Q,N$ before a component-facing consumer can inspect the result.

Use budget associativity from \autoref{thm:regular-cauchy-finite-product-budget-associativity}. Regrouping the displayed fold may expose the requested component slot, but it preserves the same dyadic observations, product-budget ledger, final regular readback, and Real seal.

The structural rows $H,C,Q,N$ transport, replay, source, and name only that displayed route. Since the carrier has no host finite-product coordinate, quotient stream equality, selected component representative, trichotomy, or ambient completeness theorem, projection stability is exhausted by the finite-product packet itself.
\end{proof}

\begin{theorem}[Regular Cauchy finite product Real seal non-escape]\label{thm:regular-cauchy-finite-product-real-seal-nonescape}
For every accepted $\RegularCauchyFiniteProductUp$ carrier $K$, the $\RealUp$ seal row exposed by $K$ is a downstream seal for the displayed finite route
$$
I,S,W,D,P,R .
$$
It exposes no host finite product, no quotient stream equality, no selected limit, no trichotomy, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Inspect the carrier boundary. The seal row $E$ appears only after the index, source, synchronized window, dyadic observation, product-budget, and regular readback rows.

The transport and replay rows $H$ and $C$ preserve this order. They can move or replay the displayed route, but they do not add an independent product coordinate or a host equality coordinate.

The provenance and local naming rows $Q$ and $N$ cite the same dependencies. Since the carrier has no coordinate for a host finite product, quotient stream equality, selected limit, trichotomy, or ambient completeness theorem, the $\RealUp$ seal cannot export any of them.
\end{proof}

\begin{theorem}[Regular Cauchy finite product projection roundtrip]
\label{thm:regular-cauchy-finite-product-projection-roundtrip}
For every accepted $\RegularCauchyFiniteProductUp$ carrier $K=(I,S,W,D,P,R,E,H,C,Q,N)$, any left or right projection read consumed by $\RegularCauchyProductProjectionUp$ factors back through the same finite index row $I$, source family $S$, synchronized window family $W$, dyadic observations $D$, product-budget ledger $P$, and final readback $R$. The projection packet may expose component readbacks, but it cannot introduce a host product, selected component representative, or quotient stream equality.
\end{theorem}
\begin{proof}
Begin with an accepted finite-product carrier $K=(I,S,W,D,P,R,E,H,C,Q,N)$ and a projection read consumed by \autoref{ch:concrete-instances-regular-cauchy-product-projection-namecert}. The projection can name a left or right component only after it names the product packet from which that component is read.

Apply the tail-budget theorem \autoref{thm:regular-cauchy-finite-product-tail-budget}. The product-facing read factors through $I,S,W,D,P,R$ before any $\RealUp$ seal or component-facing export is available.

Apply budget associativity from \autoref{thm:regular-cauchy-finite-product-budget-associativity}. Regrouping the binary fold may expose the component position needed by the projection packet, but it preserves the same synchronized windows, dyadic observations, product-budget ledger, final readback, and seal route.

Finally use the Real seal non-escape theorem \autoref{thm:regular-cauchy-finite-product-real-seal-nonescape}. The projection packet may expose component readbacks downstream of the displayed finite product route, but no host product, selected component representative, or quotient stream equality is present in the carrier.
\end{proof}

\begin{theorem}[Regular Cauchy finite product diagonal seal]
\label{thm:regular-cauchy-finite-product-diagonal-seal}
For every accepted $\RegularCauchyFiniteProductUp$ carrier $K=(I,S,W,D,P,R,E,H,C,Q,N)$, any diagonal read or component projection read from $K$ preserves the same synchronized $\StreamNameUp$ windows $W$, $\DyadicRatCoreUp$ observations $D$, product-budget ledger $P$, final $\RegSeqRatUp$ readback $R$, and terminal $\RealUp$ seal $E$. Thus a finite-product consumer may reuse the projected route as a sealed $\RegSeqRatUp$ and $\RealUp$ input, but it cannot introduce a host product, selected component representative, quotient stream equality, trichotomy, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:regular-cauchy-finite-product-namecert-obligations}. They order every accepted carrier through the finite unary index row, component sources, synchronized windows, dyadic observations, product-budget ledger, final readback, seal, transport, replay, provenance, and local name.

Induct over the displayed finite fold route. The base read is one component source with its synchronized window and dyadic observation rows, so the readback and seal are exactly the rows displayed in $R$ and $E$.

For the fold step, use budget associativity from \autoref{thm:regular-cauchy-finite-product-budget-associativity}. Regrouping a binary product exposes the component or diagonal position without changing $W,D,P,R,E$.

Finally apply the Real seal non-escape theorem \autoref{thm:regular-cauchy-finite-product-real-seal-nonescape} and the projection roundtrip \autoref{thm:regular-cauchy-finite-product-projection-roundtrip}. The projected read still passes through the same finite product route before it reaches $\RegSeqRatUp$ readback or $\RealUp$ sealing, so no excluded host equality or completion object is exported.
\end{proof}

\begin{theorem}[Regular Cauchy finite product classifier bridge]
\label{thm:regular-cauchy-finite-product-classifier-bridge}
Two accepted $\RegularCauchyFiniteProductUp$ packets
$$
K=(I,S,W,D,P,R,E,H,C,Q,N)
\quad\text{and}\quad
K'=(I',S',W',D',P',R',E',H',C',Q',N')
$$
are classifier-equal exactly when the finite unary index rows $I,I'$ match, the component $\RegSeqRatUp$ classifiers on $S,S'$ agree slotwise, the synchronized $\StreamNameUp$ window classifiers on $W,W'$ agree for component, intermediate, and final reads, the $\DyadicRatCoreUp$ tolerance and readback ledgers $D,P$ and $D',P'$ are equal as displayed budget data, and the downstream $\RealUp$ seal route through $R,E,H,C,Q,N$ is the same as the route through $R',E',H',C',Q',N'$. This correspondence is the finite-product classifier surface consumed by product regular-Cauchy limit certificates and Real algebra finite-product certificates.
\end{theorem}
\begin{proof}
For the forward direction, project both accepted carriers using \autoref{def:regular-cauchy-finite-product-carrier}. The classifier for an accepted packet has no coordinate outside $I,S,W,D,P,R,E,H,C,Q,N$, so equality of packet classifiers can be read only from the listed rows.

The first projection reads the finite unary index row. Once $I$ and $I'$ match, the component slots are aligned, and the component classifier comparison is forced to be slotwise comparison of the $\RegSeqRatUp$ source family $S$ against $S'$.

Next read the synchronized window and dyadic budget rows. The window classifiers on $W,W'$ cover the component, intermediate, and final product reads, while the ledgers $D,P$ and $D',P'$ record the tolerance cells, readback cells, radius allocation, fold schedule, and slack account. These are the only budget rows available to the classifier.

Finally, use the Real seal non-escape theorem \autoref{thm:regular-cauchy-finite-product-real-seal-nonescape}. The route through $R,E,H,C,Q,N$ cannot export a host finite product or quotient stream equality, so downstream classifier agreement is exactly agreement of that displayed seal route.

For the reverse direction, rebuild the packet classifier from the matching rows. The common finite index row aligns the sources; the component $\RegSeqRatUp$ classifiers and synchronized $\StreamNameUp$ window classifiers rebuild the inspected fold; the equal dyadic tolerance and budget ledgers rebuild the product-accounting part; and the common route through $R,E,H,C,Q,N$ supplies the same terminal $\RealUp$ seal, transport, replay, provenance, and local name.

The diagonal seal theorem \autoref{thm:regular-cauchy-finite-product-diagonal-seal} then shows that every product-facing consumer sees the same projected route. Since the carrier exposes no additional classifier coordinate, the rebuilt rows are sufficient for classifier equality, and the same bridge is available to downstream regular-Cauchy limit and Real algebra finite-product consumers.
\end{proof}

\falsifiablePrediction{Every $\RegularCauchyFiniteProductUp$ product-facing read factors through a finite unary index row, component RegSeqRat sources, synchronized StreamName windows, DyadicRatCore observations, a finite product-budget ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{regseqrat, streamname, dyadicratcore, real, regularcauchyproduct, cauchyproduct: $\RegularCauchyFiniteProductUp$ is not bijective to any listed sibling because it jointly carries a finite unary product index, synchronized multi-source windows, dyadic product-budget accounting, final RegSeqRat readback, RealUp sealing, transport, continuation, provenance, and local naming.}

\closureat{RegularCauchyFiniteProductUp}{seedStr}

\begin{closurestatus}{\RegularCauchyFiniteProductUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-finite-product-carrier}, \autoref{thm:regular-cauchy-finite-product-namecert-obligations}, \autoref{thm:regular-cauchy-finite-product-tail-budget}, \autoref{thm:regular-cauchy-finite-product-budget-associativity}, and \autoref{thm:regular-cauchy-finite-product-real-seal-nonescape} seed the finite product route from displayed regular Cauchy sources through synchronized windows, dyadic product budgets, final RegSeqRat readback, and RealUp sealing.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.RegularCauchyFiniteProductUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host finite products, quotient stream equality, selected limits, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tuple-window coverage, budget exactness, readback stability, seal non-escape, and local naming for BEDC.Derived.RegularCauchyFiniteProductUp.}
  \constructivestory{A $\RegularCauchyFiniteProductUp$ packet is generated from a finite unary index row, component RegSeqRat source rows, synchronized StreamName windows, DyadicRatCore observations, a finite product-budget ledger, final RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
