\begin{theorem}[Real stream finite-prefix exactness]
\label{thm:real-stream-finite-prefix-exactness}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$,
$$
\mathsf{RealStreamClassifier}(x,y)
\quad\Longleftrightarrow\quad
\forall n,\ \mathsf{RealStreamPrefixClassifier}(x,y,n).
$$
\end{theorem}
\begin{proof}
For the forward direction, apply
\autoref{thm:real-stream-classifier-prefix}. The pointwise stream classifier
supplies exactly the rational-history classifier needed at each endpoint of the
recursive prefix construction.

For the reverse direction, assume every finite prefix is classified and fix an
observation index $n$. Apply the hypothesis at $n$, then use
\autoref{thm:real-stream-prefix-classifier-endpoint} to recover
$\mathsf{RatHistoryClassifier}(x(n),y(n))$. Since $n$ was arbitrary, these
endpoint classifiers are precisely $\mathsf{RealStreamClassifier}(x,y)$.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealStreamClassifier\_finite\_prefix\_exactness}

\begin{theorem}[Real stream classifier symmetry]
\label{thm:real-stream-classifier-symmetry}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, if
$\mathsf{RealStreamClassifier}(x,y)$, then
$\mathsf{RealStreamClassifier}(y,x)$.
\end{theorem}
\begin{proof}
Fix an observation index. The stream classifier supplies the rational-history
classifier at that index, and rational-history classifier symmetry reverses it.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealStreamClassifier\_symm}

\begin{theorem}[Real stream classifier transitivity]
\label{thm:real-stream-classifier-transitivity}
For rational-observation streams $x,y,z:\mathbb{N}\to\Hist$, if
$\mathsf{RealStreamClassifier}(x,y)$ and
$\mathsf{RealStreamClassifier}(y,z)$, then
$\mathsf{RealStreamClassifier}(x,z)$.
\end{theorem}
\begin{proof}
Fix an observation index. The two stream classifiers give the two
rational-history classifier witnesses at that index, and rational-history
classifier transitivity composes them.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealStreamClassifier\_trans}

\begin{theorem}[Real stream classifier certificate fields]
\label{thm:real-stream-classifier-certificate-fields}
For rational-observation streams $x,y,z:\mathbb{N}\to\Hist$, the pointwise
stream classifier supplies the following stability certificate fields:
\begin{enumerate}
  \item if $\forall n,\ \mathsf{RatHistoryCarrier}(x(n))$, then
  $\mathsf{RealStreamClassifier}(x,x)$;
  \item if $\mathsf{RealStreamClassifier}(x,y)$, then for every $n$ both
  $\mathsf{RatHistoryCarrier}(x(n))$ and $\mathsf{RatHistoryCarrier}(y(n))$;
  \item if $\mathsf{RealStreamClassifier}(x,y)$, then
  $\mathsf{RealStreamClassifier}(y,x)$;
  \item if $\mathsf{RealStreamClassifier}(x,y)$ and
  $\mathsf{RealStreamClassifier}(y,z)$, then
  $\mathsf{RealStreamClassifier}(x,z)$.
\end{enumerate}
\end{theorem}
\begin{proof}
For reflexivity, fix the stream $x$ and its pointwise rational-history carrier
witness. Apply \autoref{thm:real-stream-prefix-classifier-refl} at every finite
prefix. The reverse direction of
\autoref{thm:real-stream-finite-prefix-exactness} then repacks these prefix
witnesses as $\mathsf{RealStreamClassifier}(x,x)$.

For endpoint carrier readback, unfold the pointwise stream classifier and fix an
index $n$. The classifier at $n$ is a $\mathsf{RatHistoryClassifier}(x(n),y(n))$
witness, and unpacking the rational-history classifier gives both endpoint
carrier facts.

The symmetry field is exactly
\autoref{thm:real-stream-classifier-symmetry}. The transitivity field is exactly
\autoref{thm:real-stream-classifier-transitivity}. These four clauses are
therefore available as the certificate-level stability package for the stream
classifier.
\end{proof}

\begin{theorem}[Real stream classifier hsame transport]
\label{thm:real-stream-classifier-hsame-transport}
For rational-observation streams $x,x',y,y':\mathbb{N}\to\Hist$, if
$\forall n,\ \hsame(x(n),x'(n))$ and
$\forall n,\ \hsame(y(n),y'(n))$, then
$$
\mathsf{RealStreamClassifier}(x,y)
\Longleftrightarrow
\mathsf{RealStreamClassifier}(x',y').
$$
\end{theorem}
\begin{proof}
For the forward direction, assume $\mathsf{RealStreamClassifier}(x,y)$. By the
forward direction of \autoref{thm:real-stream-finite-prefix-exactness}, every
finite prefix $\mathsf{RealStreamPrefixClassifier}(x,y,n)$ is classified.

For each prefix index $n$, apply
\autoref{thm:real-stream-prefix-classifier-hsame-transport} with the two
pointwise $\hsame$ hypotheses. This transports the prefix classifier from
$(x,y)$ to $(x',y')$ at the same index.

Since the transported prefix witness is available for every $n$, the reverse
direction of \autoref{thm:real-stream-finite-prefix-exactness} reassembles
these finite-prefix witnesses into
$\mathsf{RealStreamClassifier}(x',y')$.

For the reverse direction, assume $\mathsf{RealStreamClassifier}(x',y')$. The
same finite-prefix exactness theorem gives
$\mathsf{RealStreamPrefixClassifier}(x',y',n)$ for every $n$.

For each prefix index $n$, use the symmetry of the pointwise $\hsame$
witnesses to obtain $\hsame(x'(n),x(n))$ and $\hsame(y'(n),y(n))$. Applying
\autoref{thm:real-stream-prefix-classifier-hsame-transport} with these
symmetric witnesses transports the prefix classifier from $(x',y')$ back to
$(x,y)$.

The reverse direction of \autoref{thm:real-stream-finite-prefix-exactness}
then reassembles the transported finite-prefix witnesses into
$\mathsf{RealStreamClassifier}(x,y)$.
\end{proof}
