\begin{theorem}[Real stream finite-window overlap partition]
\label{thm:real-stream-window-overlap-partition}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$ and indices
$n,m,r$,
$$
\mathsf{RealStreamWindowClassifier}(x,y,n,m+r)
\Longleftrightarrow
\mathsf{RealStreamWindowClassifier}(x,y,n,m)\land
\mathsf{RealStreamWindowClassifier}(x,y,n+m,r).
$$
\end{theorem}
\begin{proof}
For the forward direction, assume the wide window
$\mathsf{RealStreamWindowClassifier}(x,y,n,m+r)$. Apply
\autoref{thm:real-stream-window-subwindow-extraction} with shift $0$ and
radius $m$; the bound $0+m\le m+r$ extracts the left window
$\mathsf{RealStreamWindowClassifier}(x,y,n,m)$.

Apply \autoref{thm:real-stream-window-subwindow-extraction} again with shift
$m$ and radius $r$. The bound $m+r\le m+r$ extracts the right overlapping
window $\mathsf{RealStreamWindowClassifier}(x,y,n+m,r)$. These two extracted
windows form the displayed conjunction.

For the reverse direction, assume the two overlapping windows. Unfold
Definition~\ref{def:real-stream-finite-window-classifier} and fix a selected
offset $k\le m+r$. It remains to produce the RatUp endpoint classifier at
$n+k$.

If $k\le m$, the left window applies directly at offset $k$ and gives
$$
\mathsf{RatHistoryClassifier}(x(n+k),y(n+k)).
$$

In the remaining bounded-offset case, write $k=m+j$ with $j\le r$. The right
window applies at offset $j$ and gives
$$
\mathsf{RatHistoryClassifier}(x((n+m)+j),y((n+m)+j)).
$$
The arithmetic identity $(n+m)+j=n+(m+j)=n+k$ identifies this endpoint with
the selected endpoint of the wide window.

The two offset cases cover every $k\le m+r$, with the boundary endpoint
$k=m$ shared by both windows. Hence the collected endpoint classifiers repack
as $\mathsf{RealStreamWindowClassifier}(x,y,n,m+r)$.
\end{proof}

The ten-field fit is: traditional target overlapping finite rational
observation intervals; BEDC source $\mathsf{RealStreamWindowClassifier}$ over
RatUp endpoint classifiers; carrier rational-observation streams; classifier
finite-window predicate; stability by subwindow extraction and bounded-offset
splitting; ledger anchor, overlap radius, right radius, shared boundary, and
selected offset; core theorem
\autoref{thm:real-stream-window-overlap-partition}; exactness the displayed
equivalence; standard bridge overlapping finite RegSeqRat observation
intervals; status $\mathsf{ProofTarget}$.

\begin{theorem}[Real stream finite-window overlap boundary readback package]
\label{thm:real-stream-window-overlap-boundary-readback-package}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, indices $n,m,r$,
and histories $a,b,z_X,z_Y:\Hist$, assume
$\mathsf{RealStreamWindowClassifier}(x,y,n,m+r)$,
$\hsame(x(n+m),\Eone(a))$, and $\hsame(y(n+m),\Eone(b))$. Then the shared
boundary endpoint at $n+m$ carries the following package:
\begin{enumerate}
\item $\mathsf{RealStreamWindowClassifier}(x,y,n,m)$;
\item $\mathsf{RealStreamWindowClassifier}(x,y,n+m,r)$;
\item $\mathsf{RatHistoryClassifier}(\Eone(a),\Eone(b))$;
\item $\mathsf{UnaryHistory}(a)\land \mathsf{UnaryHistory}(b)\land
\hsame(a,b)$;
\item $\mathsf{PositiveUnaryDenominator}(x(n+m))\land
\mathsf{PositiveUnaryDenominator}(y(n+m))$;
\item $\mathsf{UnaryHistory}(x(n+m))\land
\mathsf{UnaryHistory}(y(n+m))\land
(\hsame(x(n+m),\emp)\to\mathsf{False})\land
(\hsame(y(n+m),\emp)\to\mathsf{False})$;
\item $(\hsame(x(n+m),\Ezero(z_X))\to\mathsf{False})\land
(\hsame(y(n+m),\Ezero(z_Y))\to\mathsf{False})$.
\end{enumerate}
\end{theorem}
\begin{proof}
Apply the forward direction of
\autoref{thm:real-stream-window-overlap-partition} to the wide window
$\mathsf{RealStreamWindowClassifier}(x,y,n,m+r)$. This produces the left
window over $(n,m)$ and the right overlapping window over $(n+m,r)$.

The shared boundary is the selected offset $m$ inside the wide window. Since
$m\le m+r$, \autoref{thm:real-stream-window-selected-full-shape-readback-package}
applies to the wide window with $k=m$ and to the displayed one-extension
comparisons at $x(n+m)$ and $y(n+m)$.

That selected readback package gives
$\mathsf{RatHistoryClassifier}(\Eone(a),\Eone(b))$, the two unary tail
witnesses with $\hsame(a,b)$, the positive denominator rows, the unary and
nonempty endpoint rows, and the two zero-head exclusions. Repack these rows
with the two windows obtained from the overlap partition.
\end{proof}

The ten-field fit is: traditional target shared boundaries of finite RegSeqRat
observation intervals; BEDC source RealUp finite windows, RatUp endpoint
classifier, and StreamNameUp observation schedule; carrier rational-observation
streams; classifier $\mathsf{RealStreamWindowClassifier}$ with the selected
boundary RatUp package; stability by overlap partition and selected endpoint
readback; ledger anchor, left radius, right radius, shared endpoint, and
displayed one-extension witnesses; core theorems
\autoref{thm:real-stream-window-overlap-partition} and
\autoref{thm:real-stream-window-selected-full-shape-readback-package};
exactness the displayed boundary package; standard bridge RealUp finite-window
exhaustion boundary for RegSeqRat finite observations; status
$\mathsf{ProofTarget}$.

\begin{theorem}[Real stream finite-window three-piece partition]
\label{thm:real-stream-window-three-piece-partition}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$ and indices
$n,m,r,s$,
$$
\mathsf{RealStreamWindowClassifier}(x,y,n,m+1+r+1+s)
\Longleftrightarrow
\mathsf{RealStreamWindowClassifier}(x,y,n,m)\land
\mathsf{RealStreamWindowClassifier}(x,y,n+(m+1),r)\land
\mathsf{RealStreamWindowClassifier}(x,y,n+(m+1)+(r+1),s).
$$
\end{theorem}
\begin{proof}
For the forward direction, assume the wide window
$\mathsf{RealStreamWindowClassifier}(x,y,n,m+1+r+1+s)$. Apply
\autoref{thm:real-stream-window-adjacent-partition} with right radius
$r+1+s$ to split it into the left window at $(n,m)$ and the remaining right
block at $(n+(m+1),r+1+s)$.

Apply \autoref{thm:real-stream-window-adjacent-partition} again to that
remaining block, now with left radius $r$ and right radius $s$. This gives the
middle window at $(n+(m+1),r)$ and the right window at
$(n+(m+1)+(r+1),s)$, and the three extracted windows form the displayed
conjunction.

For the reverse direction, assume the three displayed windows. Apply the
reverse direction of \autoref{thm:real-stream-window-adjacent-partition} to
the middle and right windows, producing the combined right block
$\mathsf{RealStreamWindowClassifier}(x,y,n+(m+1),r+1+s)$.

Apply the reverse direction of
\autoref{thm:real-stream-window-adjacent-partition} once more to the left
window and this combined right block. The result is the wide window
$\mathsf{RealStreamWindowClassifier}(x,y,n,m+1+r+1+s)$.
\end{proof}

The ten-field fit is: traditional target finite RegSeqRat observation chains;
BEDC source RealUp windows over RatUp endpoint classifiers and StreamNameUp
observation schedules; carrier rational-observation streams; classifier
$\mathsf{RealStreamWindowClassifier}$; stability by adjacent partition and
concatenation; ledger two cut points and three bounded-offset blocks; core
theorem \autoref{thm:real-stream-window-three-piece-partition}; exactness
equivalence between the wide window and the three chained windows; standard
bridge finite observation interval refinement for RealUp; status
$\mathsf{ProofTarget}$.

\begin{definition}[Real stream finite-window partition spine]
\label{def:real-stream-window-partition-spine}
For a rational-observation anchor $n$ and a total finite bound $w$, a nonempty
$\mathsf{BEDC}$ finite partition spine is a finite $\mathsf{BHist}$-coded chain
$P$ of unary radius histories $a_0,\ldots,a_{q-1}:\Hist$ together with endpoint
continuation rows. Its numeric radii $r_i$ are the unary lengths displayed by
the $a_i$, its segment anchors are
$$
n_0=n,\qquad n_{i+1}=n_i+(r_i+1),
$$
and its accumulated displayed bound is
$$
w=r_0+1+r_1+1+\cdots+1+r_{q-1}.
$$
The singleton spine has accumulated bound $r_0$ and one segment at the original
anchor. The successor spine appends one unary radius $a_i$ by a native unary
$\mathsf{append}$ display and a $\mathsf{Cont}$ row from the previous endpoint
anchor to the next endpoint anchor. Thus every segment named by $P$ is a
concrete RealUp finite window
$\mathsf{RealStreamWindowClassifier}(x,y,n_i,r_i)$, and the final accumulated
anchor is obtained only by repeated unary $\mathsf{append}$ and $\mathsf{Cont}$
composition.
\end{definition}

\begin{theorem}[Real stream finite-window partition fold]
\label{thm:real-stream-window-finite-partition-fold}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, an anchor $n$, a
total bound $w$, and a certified finite partition spine $P$ over $(n,w)$ with
segments $(n_i,r_i)$, the total window classifier is equivalent to the
conjunction of the segment classifiers named by $P$:
$$
\mathsf{RealStreamWindowClassifier}(x,y,n,w)
\Longleftrightarrow
\bigwedge_{(n_i,r_i)\in P}
\mathsf{RealStreamWindowClassifier}(x,y,n_i,r_i).
$$
For the singleton spine, the right side is the single segment classifier.
\end{theorem}
\begin{proof}
Proceed by induction on the certified partition spine $P$.

In the singleton case, the spine definition identifies the total bound with the
single segment radius. The right side is the same
$\mathsf{RealStreamWindowClassifier}(x,y,n,r_0)$ row, so the displayed
equivalence is reflexive.

For the successor step, write the predecessor spine as $P_0$ with accumulated
bound $u$ and final anchor $n+u+1$ in the displayed unary continuation ledger.
The new certified unary radius is $r$, so the successor spine displays the
total bound as $u+1+r$ and names the new final segment
$\mathsf{RealStreamWindowClassifier}(x,y,n+(u+1),r)$.

For the forward direction of the successor step, apply
\autoref{thm:real-stream-window-adjacent-partition} to the total window
$\mathsf{RealStreamWindowClassifier}(x,y,n,u+1+r)$. This gives the predecessor
wide window $\mathsf{RealStreamWindowClassifier}(x,y,n,u)$ and the new final
segment. Apply the induction hypothesis to the predecessor wide window to
obtain every segment classifier named by $P_0$, then conjoin that list with the
new final segment.

For the reverse direction, assume the conjunction over the successor spine.
Project the predecessor segment conjunction and the new final segment. The
induction hypothesis repacks the predecessor segment conjunction into
$\mathsf{RealStreamWindowClassifier}(x,y,n,u)$. Apply the reverse direction of
\autoref{thm:real-stream-window-adjacent-partition} to this predecessor window
and the new final segment, producing
$\mathsf{RealStreamWindowClassifier}(x,y,n,u+1+r)$.

The three-segment case is the displayed consistency check: taking a spine with
three radii $m,r,s$ reduces the induction twice and gives exactly
\autoref{thm:real-stream-window-three-piece-partition}. Its two displayed cut
points are the first two successor anchors in the finite spine ledger.
\end{proof}

The ten-field fit is: traditional target finite RegSeqRat observation partition
coverage; BEDC source $\mathsf{RealStreamWindowClassifier}$ plus
$\mathsf{RatHistoryClassifier}$ endpoint rows and $\mathsf{Cont}$ with unary
anchors; carrier rational-observation streams; classifier
$\mathsf{RealStreamWindowClassifier}$ over a certified finite partition spine;
stability by adjacent partition, induction on the $\mathsf{BHist}$ spine, and
unary anchor continuation; ledger total bound, segment radii, accumulated
anchors, continuation rows, and endpoint classifiers; core theorem
\autoref{thm:real-stream-window-finite-partition-fold}; exactness the displayed
fold equivalence; standard bridge RealUp and RegSeqRat finite observation
coverage; status $\mathsf{ProofTarget}$.

\begin{theorem}[RealUp finite-window partition read surface]
\label{thm:realup-window-partition-read-surface}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, an anchor $n$, a
total bound $w$, and a certified finite partition spine $P$ over $(n,w)$ with
segments $(n_i,r_i)$, the total window
$\mathsf{RealStreamWindowClassifier}(x,y,n,w)$ and the conjunction of segment
windows
$$
\bigwedge_{(n_i,r_i)\in P}
\mathsf{RealStreamWindowClassifier}(x,y,n_i,r_i)
$$
expose the same scoped $\RealUp$ certificate boundary rows. These rows are
exactly the endpoint $\RatUp$ classifiers, positive unary denominator rows,
nonempty unary endpoint rows, common e-one tail readback wherever the endpoints
are displayed as one-headed, finite $\mathsf{RealLedgerPolicy}$ rows,
DyadicRatCore observation rows, $\RegSeqRat$ spine rows, $\StreamNameUp$ request
names, $\mathsf{UnaryHistory}$ witnesses, and $\hsame$ transport rows named by
the certified window spine. Neither presentation reads quotient data, a
completion object, a metric-completeness certificate, arithmetic or order
closure, Classical data, or a standard bridge.
\end{theorem}
\begin{proof}
First transport between the two window presentations. Apply
\autoref{thm:real-stream-window-finite-partition-fold}; the total classifier at
$(n,w)$ is equivalent to the finite conjunction of the segment classifiers named
by $P$.

Now read the total presentation through the scoped boundary. Apply
\autoref{thm:realup-scoped-finite-window-read-surface} to the total window. It
identifies the endpoint $\RatUp$ rows, denominator rows, common e-one tail
readback, finite ledger rows, dyadic source rows, stream-name rows, unary
history witnesses, and $\hsame$ transport rows available at the total window.

For each segment $(n_i,r_i)$ supplied by the partition spine, apply
\autoref{thm:realup-scoped-finite-window-read-surface} again to the segment
window $\mathsf{RealStreamWindowClassifier}(x,y,n_i,r_i)$. The partition-spine
ledger records that the segment anchors and radii are obtained from the same
unary radius histories, $\mathsf{append}$ displays, and $\mathsf{Cont}$ rows
used to display the total bound, so the segment reads name only the finite
endpoint and dyadic source rows already named by the total presentation.

It remains to identify the primitive boundary. Apply
\autoref{thm:realup-finite-window-exhaustion-obligation} for the endpoint
package and dyadic finite-window source exhaustion. Apply
\autoref{thm:realup-stream-prefix-scoped-obligation-package} for the carrier,
classifier, stability, ledger, and seal rows of the primitive stream-prefix
boundary. These two packages contain exactly the rows listed in the statement
and exclude quotient, completion, metric-completeness, arithmetic, order,
Classical, and standard-bridge data, so the partitioned and total presentations
have the same scoped $\RealUp$ read surface.
\end{proof}

\begin{theorem}[RealUp finite-window partition stability package]
\label{thm:realup-window-partition-stability-package}
For rational-observation streams $x,x',y,y',z:\mathbb{N}\to\Hist$, an anchor
$n$, a total bound $w$, and a certified finite partition spine $P$ over
$(n,w)$ with segments $(n_i,r_i)$, the four stability rows of
$\mathsf{RealStreamWindowClassifier}$ commute with the correspondence between
the total window at $(n,w)$ and the segment windows named by $P$.

Concretely, both the total presentation
$\mathsf{RealStreamWindowClassifier}(-,-,n,w)$ and the segment presentation
$$
\bigwedge_{(n_i,r_i)\in P}
\mathsf{RealStreamWindowClassifier}(-,-,n_i,r_i)
$$
expose the same scoped stability package:
\begin{enumerate}
  \item reflexivity from endpoint carrier rows for each displayed observation;
  \item symmetry of the window classifier;
  \item transitivity through the middle stream $y$;
  \item pointwise $\hsame$ transport from $(x,y)$ to $(x',y')$ over the
  displayed observations.
\end{enumerate}
The exposed certificate boundary in either presentation is exactly the scoped
read surface of \autoref{thm:realup-window-partition-read-surface}: endpoint
$\RatUp$ rows, $\mathsf{DyadicRatCore}$ observation rows, $\RegSeqRat$ spine
rows, $\StreamNameUp$ request names, $\mathsf{UnaryHistory}$ witnesses,
$\hsame$ transport rows, and the finite ledger rows named by the certified
partition spine.
\end{theorem}
\begin{proof}
First identify the two window presentations. Apply
\autoref{thm:real-stream-window-finite-partition-fold} to the certified spine
$P$. It gives the equivalence between the total classifier at $(n,w)$ and the
finite conjunction of segment classifiers at the anchors and radii listed by
$P$.

Next apply \autoref{thm:real-stream-window-classifier-stability-package} to the
total window. Its four rows give reflexivity from the carrier observations,
symmetry, transitivity through $y$, and pointwise $\hsame$ transport from
$(x,y)$ to $(x',y')$ on every offset $k\le w$.

For the segment presentation, apply the same stability package to each segment
window $\mathsf{RealStreamWindowClassifier}(-,-,n_i,r_i)$. The spine ledger
records that every displayed segment offset is one of the observations in the
total window, and the finite fold records the reverse containment by collecting
the segment windows back into the total classifier.

Finally apply \autoref{thm:realup-window-partition-read-surface}. It identifies
the public rows exposed by the total presentation and by the partitioned
presentation as the same endpoint $\RatUp$, $\mathsf{DyadicRatCore}$,
$\RegSeqRat$, $\StreamNameUp$, $\mathsf{UnaryHistory}$, $\hsame$, and ledger
rows. Therefore transporting any of the four stability rows across the fold
does not expose additional data and does not lose any scoped row from the
listed $\RealUp$ boundary.
\end{proof}

\begin{theorem}[Real stream finite-window partition refinement transitivity]
\label{thm:real-stream-window-partition-refinement-transitivity}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, a total anchor $n$,
a total bound $w$, and certified finite partition spines $P,Q$ over $(n,w)$,
suppose every segment of $Q$ is displayed in the ledger as a consecutive union
of segments of $P$. If every $P$-segment $(n_i,r_i)$ carries
$\mathsf{RealStreamWindowClassifier}(x,y,n_i,r_i)$, then every $Q$-segment
$(m_j,s_j)$ carries $\mathsf{RealStreamWindowClassifier}(x,y,m_j,s_j)$.

Equivalently, the finite ledger exposed by the fine partition $P$ refines the
coarser partition ledger $Q$ without changing any endpoint $\RatUp$
classifier, dyadic source row, stream-name row, unary witness, $\hsame$
transport row, or continuation ledger entry at the visible boundary.

The ten-field fit is: name $\mathsf{RealStreamWindow}$ refinement
transitivity; BEDC source
$\mathsf{BHist}+\RatUp+\StreamNameUp+\mathsf{RealStreamWindowClassifier}$;
carrier the certified finite partition spine; classifier
$\mathsf{RealStreamWindowClassifier}$; pattern consecutive-union refinement of
window spines; stability the four classifier rows exposed by
\autoref{thm:realup-window-partition-stability-package}; ledger the refinement
witness from fine rows to coarse rows; exactness the unchanged $\RatUp$
endpoint classifier surface; core theorem
\autoref{thm:real-stream-window-partition-refinement-transitivity}; downstream
consumer $\RealUp$ finite-window certificate closure.
\end{theorem}
\begin{proof}
Induct on the coarser spine $Q$. The empty spine has no segment to certify, and
the ledger refinement witness contributes no visible row.

For a nonempty coarser spine, read the head segment $(m_j,s_j)$ as the
consecutive subspine of $P$ selected by the refinement ledger. Apply
\autoref{thm:real-stream-window-finite-partition-fold} to that subspine. The
given classifiers on the fine $P$-segments fold into
$\mathsf{RealStreamWindowClassifier}(x,y,m_j,s_j)$.

Now repack the visible rows for this coarse segment. Apply
\autoref{thm:realup-window-partition-read-surface} to identify the endpoint
$\RatUp$ rows, dyadic source rows, stream-name rows, unary witnesses, $\hsame$
transport rows, and finite ledger entries exposed by the fine subspine and by
the coarse segment as the same scoped read surface.

The stability fields are transported across this repacking by
\autoref{thm:realup-window-partition-stability-package}. Removing the consumed
fine subspine leaves the tail of $P$ refining the tail of $Q$, so the induction
hypothesis certifies every remaining coarse segment. Combining the head
certificate with the tail certificates gives the claimed refinement
transitivity.
\end{proof}
