\begin{theorem}[RealUp finite-window exhaustion obligation]
\label{thm:realup-finite-window-exhaustion-obligation}
At the RealUp obligation boundary, the finite-window observation field is
supplied by the conjunction of
$\mathsf{RealStreamClassifier\_finite\_prefix\_endpoint\_denominator\_package}$,
$\mathsf{RealStreamPrefixClassifier\_truncated\_endpoint\_denominator\_package}$,
$\mathsf{RealStreamPrefixClassifier\_truncated\_endpoint\_common\_e1\_tail\_readback}$,
and the $\mathsf{RegSeqRat}$ finite-window dyadic source exhaustion package.
Consequently every selected finite $\RealUp$ observation window exposes
endpoint $\RatUp$ classifiers, positive unary denominators, nonempty unary
endpoint rows, common e-one tail readback, and exactly the
$\mathsf{DyadicRatCore}$ source rows consumed by the $\RealUp$ seal, with no
data outside the carriers, classifiers, stability rows, and ledger rows listed
in \autoref{thm:realup-scoped-certificate-boundary}.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealupFiniteWindowExhaustionObligation}
\begin{proof}
First collect the endpoint denominator face. Apply
\autoref{thm:real-stream-classifier-finite-prefix-endpoint-denominator-package}
to the selected finite prefix. It supplies the endpoint $\RatUp$ classifier,
the positive unary denominator witnesses, the unary endpoint rows, and the
nonempty endpoint exclusions needed at the selected observation.

Next pass to truncated prefixes. Apply the truncated endpoint denominator
package recorded by
\autoref{thm:real-stream-prefix-finite-tail-transported-endpoint-denominator-package}.
This transports the same endpoint denominator data through the finite tail
presentation used by the stream-prefix carrier and classifier rows.

Now read the selected one-headed tails. Apply
\autoref{thm:real-stream-prefix-truncated-endpoint-common-e1-tail-readback};
the truncated endpoint package gives the hypotheses needed to expose common
e-one tails at the two selected endpoint histories.

Finally identify the consumed source rows. Apply
\autoref{thm:regseqrat-finite-window-dyadic-source-exhaustion}. It states that
the selected bounded RegSeqRat observation reads exactly the two
$\mathsf{DyadicRatCoreObservationRow}$ endpoint sources and the scoped
carrier, classifier, stability, and finite ledger faces named by the dyadic
source package. These are precisely the rows allowed by
\autoref{thm:realup-scoped-certificate-boundary}; hence the finite-window observation
field consumes no data outside that boundary.
\end{proof}

\begin{theorem}[RealUp StreamName RegSeqRat dyadic handoff exhaustion]
\label{thm:realup-streamname-regseqrat-dyadic-handoff-exhaustion}
Every $\RealUp$ finite-window observation whose StreamName face is a
$\RegSeqRat$ handoff factors through exactly the displayed finite source
surface: the $\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the selected
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$ rows,
the endpoint $\RatUp$ denominator rows, the accepted $\RegSeqRat$ spine, the
DyadicRatCore source rows, the shown $\hsame/\Cont/\Pkg$ ledger, and the
$\mathsf{RealLedgerPolicy}$ row.

This factorization is finite-row only. It exports no completion object,
quotient representative, $\mathsf{Classical}$ representative,
metric-completeness certificate, arithmetic or order operation, or
standard-bridge row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:realup-finite-window-exhaustion-obligation}. It
reduces the selected $\RealUp$ observation to endpoint denominator rows,
positive unary denominator witnesses, common e-one tail readback, and the
DyadicRatCore source rows supplied by the accepted $\RegSeqRat$ finite-window
dyadic package.

Next apply \autoref{thm:streamname-regseqrat-common-window-transport}. The
StreamName face of the same observation contributes only the finite-window
classifier row, the shared $\mathsf{ProbeBundle}$, the selected
$\mathsf{InBundle}/\mathsf{UnaryHistory}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, and the displayed
$\hsame/\Cont/\Pkg$ provenance that feeds the accepted spine.

Finally use \autoref{thm:streamname-tail-window-coverage-exhaustion}. The
tail-window packet admits no consumer row beyond the displayed classifier,
bundle, unary-history, pointwise rational-history, $\RegSeqRat$,
DyadicRatCore, and $\mathsf{RealLedgerPolicy}$ rows. Therefore the
$\RealUp$ finite-window observation factors through exactly the stated handoff
surface, and completion, quotient, $\mathsf{Classical}$ representative,
metric-completeness, arithmetic or order, and standard-bridge rows remain
outside the finite ledger.
\end{proof}

\begin{theorem}[RealUp refinement envelope reindexed consumer invariance]
\label{thm:realup-refinement-envelope-reindexed-consumer-invariance}
Let $E$ be a $\RealUp$ finite-window refinement envelope over a fixed
$\StreamNameUp$ source, and let $P$ be a
$\StreamNameUp$--$\RegSeqRat$ reindexed window package whose selected rational
classifier rows feed a certified window $W$ carried by $E$. The downstream
$\RegSeqRat$ handoff determined by $P$ and the finite-window $\RealUp$ seal
read determined by $W$ factor through the same envelope-facing rows:
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$ rows,
the endpoint denominator rows, the $\mathsf{DyadicRatCore}$ source rows, the
shared $\hsame$ ledger, and the $\mathsf{RealLedgerPolicy}$ boundary.
Consequently the reindexed handoff and the carried seal expose one public read
surface, with no exported host index, quotient witness, completion object, or
unrecorded stream row.
\end{theorem}
\begin{proof}
Begin with the reindexed package $P$. By
\autoref{thm:streamname-regseqrat-reindexed-window-exhaustion}, its selected
rational rows are exhausted by the reindexed $\StreamNameUp$ finite-window
classifier rows, the probe and unary-history rows, the endpoint denominator
rows, and the dyadic source rows visible in the window.

Next apply
\autoref{thm:realup-streamname-regseqrat-reindexed-ledger-handoff}. The
$\RegSeqRat$ consumer handoff reads those rows through the same shared
$\hsame$ ledger and the same $\mathsf{RealLedgerPolicy}$ boundary used by the
carried $\RealUp$ window.

Finally use
\autoref{thm:realup-finite-window-refinement-envelope-consumer-coverage} for
the carried window $W$ inside $E$. That theorem forces both the
$\RegSeqRat$ handoff and the finite-window $\RealUp$ seal through exactly the
rows stored in the refinement envelope.

The listed envelope rows therefore form the common public surface. Since the
envelope boundary contains no slot for a host index, quotient witness,
completion object, or unrecorded stream datum, none of those objects can be
exported by either consumer.
\end{proof}

\begin{theorem}[RealUp StreamName window determinacy boundary]
\label{thm:realup-streamname-window-determinacy-boundary}
Let two finite-window observations be admitted by the $\RealUp$ seal through
the same selected unary observation and the same
$\mathsf{RatStreamNameFiniteWindowClassifier}$ endpoint package. Then the two
observations expose the same endpoint $\RatUp$ classifier rows, the same
positive denominator witnesses, the same common e-one tail readbacks, and the
same $\mathsf{DyadicRatCore}$ source rows, up to the displayed $\hsame$ ledger
rows permitted by \autoref{thm:realup-scoped-certificate-boundary}. No host
$\mathsf{Nat}$ index, host function, quotient, or unrecorded stream object is
available to separate the two exposed windows.
\end{theorem}
\begin{proof}
Begin with the two accepted finite-window observations. Apply
\autoref{thm:realup-streamname-finite-window-ledger-boundary} to each one. The
only exposed rows are the selected unary observation, the pointwise
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the endpoint denominator
rows, and the dyadic source rows named by the finite-window obligation.

Now use the common StreamName package. The structural laws of
\autoref{thm:rat-stream-name-finite-window-structural-laws} and the selected
full-endpoint package of
\autoref{thm:rat-stream-name-finite-window-selected-full-endpoint-package}
identify the two selected observations and their endpoint classifier rows by
the displayed $\hsame$ ledger rows. Thus the endpoint $\RatUp$ classifiers and
positive denominator witnesses are the same readable rows of the package.

Finally repack through
\autoref{thm:realup-finite-window-exhaustion-obligation}. The common endpoint
package supplies the hypotheses for the common e-one tail readbacks, and the
dyadic source exhaustion supplies the same $\mathsf{DyadicRatCore}$ source
rows. Since \autoref{thm:realup-scoped-certificate-boundary} permits only these
carrier, classifier, stability, and finite ledger rows, the two windows have
the same exposed RealUp seal ledger.
\end{proof}

\begin{theorem}[RealUp finite-window coverage and determinacy package]
\label{thm:realup-finite-window-coverage-determinacy-package}
Every finite $\RealUp$ observation admitted through the $\StreamNameUp$
finite-window seal factors through one package of public rows: the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the selected
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, the
$\mathsf{UnaryHistory}$ observation, the endpoint $\RatUp$ denominator rows,
the $\mathsf{DyadicRatCore}$ source rows, the displayed $\hsame$ ledger, and
the finite $\mathsf{RealLedgerPolicy}$ boundary. Moreover, if two admitted
reads use the same selected unary observation and the same endpoint package,
then their exposed dyadic source rows agree up to that displayed $\hsame$
ledger; and any certified unary reindexing of the selected observation
preserves exactly the same package.
\end{theorem}
\begin{proof}
First apply \autoref{thm:realup-finite-window-exhaustion-obligation}. It
reduces an admitted finite $\RealUp$ window to the endpoint denominator rows,
the common e-one tail readback, and the $\mathsf{DyadicRatCore}$ source rows
visible through the finite seal.

Next apply \autoref{thm:realup-streamname-finite-window-ledger-boundary}. This
identifies the StreamName face of the same window: the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, selected probe and bundle
rows, unary-history observation, endpoint $\RatUp$ denominator rows, dyadic
source rows, and finite $\mathsf{RealLedgerPolicy}$ all sit on the same
displayed $\hsame$ ledger.

For two reads with the same selected unary observation and endpoint package,
use \autoref{thm:realup-streamname-window-determinacy-boundary}. The shared
StreamName package fixes the endpoint classifiers, denominator witnesses,
common e-one tail readbacks, and dyadic source rows up to the displayed
$\hsame$ ledger.

Finally apply
\autoref{thm:realup-finite-window-reindexed-classifier-transport}. Certified
unary reindexing transports the selected observation and classifier row while
repacking the same endpoint, source, ledger, and finite policy rows. Since no
quotient, completion object, host index, or choice datum is exported by these
four boundaries, the package is exactly the finite-window coverage and
determinacy surface stated above.
\end{proof}

\begin{theorem}[RealUp open-phase audit boundary]
\label{thm:realup-open-phase-audit-boundary}
Every paper-side Phase Real and Completion audit read that reaches
$\RealUp$ through finite windows factors through exactly the
$\StreamNameUp$ finite-window classifier, the $\RegSeqRat$ dyadic source
exhaustion, the $\mathsf{DyadicRatCore}$ source rows, the endpoint $\RatUp$
denominator rows, the displayed $\hsame$, $\Cont$, and $\Pkg$ ledger, and
the local $\NameCert$ rows. Conversely this package is sufficient for the
L10 exit boundary for those reads. It exports no quotient, selected limit,
completion theorem, countable-choice row, metric-completeness datum,
arithmetic or order extension, or standard bridge.
\end{theorem}
\begin{proof}
Apply \autoref{thm:realup-finite-window-exhaustion-obligation} to reduce any
accepted $\RealUp$ finite-window read to endpoint denominator rows, common
tail readback, and dyadic source rows.

Next apply \autoref{thm:realup-streamname-regseqrat-dyadic-handoff-exhaustion}
and \autoref{thm:realup-finite-window-coverage-determinacy-package}. These
identify the same read through the StreamName finite-window classifier,
RegSeqRat dyadic source exhaustion, DyadicRatCore source rows, endpoint
$\RatUp$ rows, displayed ledger, package provenance, and local naming rows.

The cited StreamName, RegSeqRat, and dyadic source rows already supply the
forward package read by the roadmap boundary. The non-export clauses follow
from the same finite-window exhaustion: none of quotient formation, selected
limit choice, completion closure, countable choice, metric completeness,
arithmetic or order extension, or a standard bridge is a displayed row of
the package.
\end{proof}

\begin{theorem}[RealUp StreamName finite-window ledger boundary]
\label{thm:realup-streamname-finite-window-ledger-boundary}
Every finite-window observation admitted by the $\RealUp$ seal factors through
the $\StreamNameUp$ finite-window classifier, the $\RatUp$ endpoint denominator
package, and the $\RegSeqRat$ dyadic source exhaustion rows. Its ledger is
exactly the selected unary observation, the pointwise
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the endpoint denominator
rows, and the dyadic source rows named by
\autoref{thm:realup-finite-window-exhaustion-obligation}. No host
$\mathsf{Nat}$ index, host function, quotient, or unrecorded infinite stream
object is exposed at this boundary.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealupStreamnameFiniteWindowLedgerBoundary}
\begin{proof}
Start with an observation accepted by the $\RealUp$ seal. Apply
\autoref{thm:realup-finite-window-exhaustion-obligation}; it reduces the
accepted finite window to the denominator package, truncated endpoint
readback, and $\RegSeqRat$ dyadic source rows allowed by the scoped seal.

The finite-window stream-name component is supplied by
\autoref{thm:rat-stream-name-finite-window-from-classifier},
\autoref{thm:rat-stream-name-finite-window-structural-laws}, and
\autoref{thm:rat-stream-name-finite-window-selected-full-endpoint-package}.
Together these rows identify the selected unary observation, the bundled
pointwise classifier, and the endpoint denominator package read by the window.

Finally use \autoref{thm:realup-scoped-certificate-boundary}. That boundary
permits only the listed carrier, classifier, stability, and finite ledger rows.
The StreamName rows and the dyadic source rows therefore repack into the exact
ledger stated above, while host $\mathsf{Nat}$ data, host functions, quotients,
and unrecorded infinite objects have no exported row to inspect.
\end{proof}

\begin{theorem}[RealUp finite-window reindexed classifier transport]
\label{thm:realup-finite-window-reindexed-classifier-transport}
Let $W$ be a selected finite $\RealUp$ observation window admitted through the
$\StreamNameUp$ finite-window seal ledger. Suppose $W'$ is obtained from $W$
by a certified $\StreamNameUp$ unary reindexer, and suppose the transported
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row and the selected endpoint
denominator package are present at $W'$. Then the transported window exposes
the same $\RealUp$ finite seal ledger boundary as $W$: endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readback,
$\mathsf{DyadicRatCore}$ source rows, unary-history rows, $\hsame$ transport,
and the finite $\mathsf{RealLedgerPolicy}$. The transported surface exposes
no quotient, completion, host $\mathsf{Nat}$ index, host function,
$\mathsf{Classical}$ datum, metric-completeness certificate, or standard
bridge.
\end{theorem}
\begin{proof}
Start with the certified unary reindexer. Apply
\autoref{thm:rat-stream-name-reindexing-and-map-stability} to transport the
selected $\StreamNameUp$ observation rows and their $\hsame$ stability ledger
from $W$ to $W'$.

Next apply
\autoref{thm:rat-stream-name-finite-window-reindexed-map-coverage}. The
transported finite-window classifier at $W'$ covers exactly the reindexed
unary observation rows and the selected endpoint package, so no host
$\mathsf{Nat}$ index or host function is exported by the StreamName face.

Now identify the RealUp ledger carried by the source window. By
\autoref{thm:realup-streamname-finite-window-ledger-boundary}, the original
surface of $W$ contains only the selected unary observation, the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readback,
$\mathsf{DyadicRatCore}$ source rows, and the finite
$\mathsf{RealLedgerPolicy}$ rows allowed by the seal.

Finally repack the transported rows through
\autoref{thm:realup-finite-window-exhaustion-obligation}. The scoped boundary
permits only carrier, classifier, stability, source, and finite ledger rows,
so the reindexed read surface is the same RealUp finite seal ledger boundary
and has no quotient, completion, $\mathsf{Classical}$ datum,
metric-completeness certificate, or standard bridge to inspect.
\end{proof}

\begin{theorem}[RealUp finite-window feed reindexing stability]
\label{thm:realup-finite-window-feed-reindexing-stability}
Let $W$ be a selected finite $\RealUp$ observation window admitted through the
$\StreamNameUp$ finite-window seal, and let $W'$ be obtained from $W$ by a
certified unary $\StreamNameUp$ reindexer. Suppose the reindexer preserves the
transported $\mathsf{RatStreamNameFiniteWindowClassifier}$ row at $W'$. Then
the public feed read at $W'$ is the same feed read at $W$: the selected
$\mathsf{UnaryHistory}$ observation, the $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ rows of the window, the endpoint $\RatUp$ denominator package, the
$\RegSeqRat$ handoff rows, the $\mathsf{DyadicRatCore}$ source rows, the
displayed $\hsame$ ledger, and the finite $\mathsf{RealLedgerPolicy}$
boundary.

The feed comparison exports no quotient row, completion object, host
$\mathsf{Nat}$ index, host function, metric-completeness certificate, or
standard bridge claim.
\end{theorem}
\begin{proof}
First transport the finite StreamName face. Apply
\autoref{thm:rat-stream-name-reindexing-and-map-stability} to move the
selected unary observation and its $\hsame$ ledger along the certified unary
reindexer. Then apply
\autoref{thm:rat-stream-name-finite-window-reindexed-map-coverage} to identify
the transported finite-window classifier with exactly the reindexed observation
rows and endpoint denominator package.

Next pass from classifier transport to the RealUp feed boundary. By
\autoref{thm:realup-finite-window-reindexed-classifier-transport}, the
reindexed classifier row exposes the same finite seal ledger boundary as the
source window, including the endpoint $\RatUp$ denominator rows,
$\mathsf{DyadicRatCore}$ source rows, displayed $\hsame$ transport, and finite
$\mathsf{RealLedgerPolicy}$ rows.

The RegSeqRat source face is the same public feed. Apply
\autoref{thm:realup-streamname-regseqrat-reindexed-ledger-handoff} to identify
the selected StreamName rational rows with the $\RegSeqRat$ dyadic handoff
rows read by the finite window.

Finally use \autoref{thm:realup-finite-window-exhaustion-obligation}. Its
boundary lists all carrier, classifier, source, and finite ledger rows admitted
by the selected window, including the $\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$
entries. Since no admitted row is a quotient, completion, host index, host
function, metric-completeness certificate, or standard bridge, the transported
feed has exactly the same public surface and no additional exported datum.
\end{proof}

\begin{theorem}[RealUp StreamName reindexing composition boundary]
\label{thm:realup-streamname-reindexing-composition-boundary}
Let $W$ be a selected finite $\RealUp$ observation window admitted through the
$\StreamNameUp$ finite-window seal ledger. Suppose two certified
$\StreamNameUp$ unary reindexers are applied successively to $W$, and suppose
the same selected endpoint package is also read through the single certified
composite reindexer. Then the successive read and the composite read expose the
same finite seal ledger: selected unary observation rows, the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, endpoint $\RatUp$
denominator rows, positive denominator witnesses, common e-one tail readback,
$\mathsf{DyadicRatCore}$ source rows, $\hsame$ transport, and the finite
$\mathsf{RealLedgerPolicy}$.

In particular, the composite surface has no additional quotient, completion,
host $\mathsf{Nat}$ index, host function, unrecorded stream object,
$\mathsf{Classical}$ datum, metric-completeness certificate, or standard bridge
beyond the rows already exposed by the two successive unary transports.
\end{theorem}
\begin{proof}
Start with the two certified unary reindexers. Apply
\autoref{thm:rat-stream-name-reindexing-and-map-stability} to each reindexing
step, and use the $\StreamNameUp$ reindexing composition law to identify the
successive selected unary observation rows with the rows selected by the single
composite reindexer.

Next apply
\autoref{thm:realup-finite-window-reindexed-classifier-transport} to the first
transported window and again to the second transported window. The finite
classifier, endpoint denominator package, common e-one tail readback, and
$\mathsf{DyadicRatCore}$ source rows are carried componentwise through the same
$\hsame$ transport ledger.

Finally compare both transported reads with
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. That boundary
lists the whole finite $\RealUp$ seal ledger, so the successive read and the
composite read have the same public rows and no further host-level reindexing
datum to inspect.
\end{proof}

\begin{theorem}[RealUp StreamName-RegSeqRat reindexed ledger handoff]
\label{thm:realup-streamname-regseqrat-reindexed-ledger-handoff}
Let $\mathcal{W}$ be a $\StreamNameUp$--$\RegSeqRat$ reindexed window package
whose selected rational classifier rows feed a finite $\RealUp$ observation
window $W$. Then the package exposes exactly the $\RealUp$ finite seal ledger
boundary for $W$: the selected unary observation row, the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the endpoint denominator
rows, and the $\RegSeqRat$ dyadic source rows selected by the finite window. It
exposes no host $\mathsf{Nat}$ index, host function, quotient, completion
object, or unrecorded infinite stream.
\end{theorem}
\begin{proof}
Start with the displayed reindexed window package. Apply
\autoref{thm:streamname-regseqrat-reindexed-window-exhaustion} to decompose its
visible rows into the selected unary observation, the transported
$\mathsf{RatStreamNameFiniteWindowClassifier}$ row, the endpoint denominator
rows, and the $\RegSeqRat$ source rows supplied by the package.

Next use \autoref{thm:streamname-real-regseq-finite-window-handoff}. It is the
common handoff from the StreamName finite-window face to the RegSeqRat dyadic
source face, so the selected rational classifier rows are the same rows read by
the finite $\RealUp$ observation.

Now apply \autoref{thm:realup-streamname-finite-window-ledger-boundary}. The
RealUp seal boundary admits exactly the selected unary observation, the finite
StreamName classifier row, the endpoint denominator rows, and the dyadic source
rows as public ledger entries.

Finally use \autoref{thm:streamname-regseqrat-reindexed-window-no-seal-import}.
It excludes the host index, host map, quotient, completion object, and
unrecorded stream data from the reindexed package, so the package and the
$\RealUp$ finite seal expose the same finite boundary.
\end{proof}

\begin{theorem}[RealUp finite-window exhaustion subwindow closure]
\label{thm:realup-finite-window-exhaustion-subwindow-closure}
Whenever a $\RealUp$ finite-window exhaustion package is exposed for a
$\StreamNameUp$ finite window, every certified subwindow obtained by the
$\StreamNameUp$ finite-window subwindow restriction exposes the same $\RatUp$
endpoint classifier, the same ledger boundary, and the same $\RealUp$ read
surface restricted to that subwindow. The restricted package reads only the
subwindow observation rows, the inherited
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the endpoint denominator
rows, and the $\mathsf{DyadicRatCore}$ source rows already named by the ambient
window.
\end{theorem}
\begin{proof}
Start with the ambient finite-window exhaustion package. Apply
\autoref{thm:realup-finite-window-exhaustion-obligation} to identify its
$\RatUp$ endpoint classifiers, positive denominator witnesses, common e-one
tail readbacks, and $\mathsf{DyadicRatCore}$ source rows.

Restrict the StreamName component by
\autoref{thm:rat-stream-name-finite-window-subwindow-restriction}. The certified
subwindow keeps the same pointwise
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows and only changes the
displayed finite observation domain.

Next use \autoref{thm:realup-streamname-window-determinacy-boundary}. It rules
out a second endpoint reading for the restricted window once the selected
StreamName package and endpoint denominator rows are fixed.

Finally apply
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. The ledger
boundary remains exactly the selected unary observation, the restricted
StreamName classifier row, the endpoint denominator rows, and the dyadic source
rows. Repacking these rows gives the same $\RealUp$ read surface restricted to
the certified subwindow.
\end{proof}

\begin{theorem}[RealUp finite-window exhaustion overlap closure]
\label{thm:realup-finite-window-exhaustion-overlap-closure}
Let two $\RealUp$ finite-window exhaustion packages expose certified
$\StreamNameUp$ subwindows. If the two restricted windows have a certified
common $\StreamNameUp$ subwindow overlap, then the overlap exposes the same
inherited $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the same
endpoint denominator rows, the same common e-one tail readbacks, and the same
$\mathsf{DyadicRatCore}$ source rows, up to the $\hsame$ ledger permitted by
\autoref{thm:realup-scoped-certificate-boundary}. The overlap certificate
does not expose host $\mathsf{Nat}$ indices, host functions, quotients, or
unrecorded infinite stream data.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:realup-finite-window-exhaustion-subwindow-closure} to each
ambient finite-window exhaustion package. Each restricted window therefore
reads only its subwindow observation rows, inherited
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint denominator
rows, common e-one tail readbacks, and $\mathsf{DyadicRatCore}$ source rows.

Now restrict both sides to the certified common $\StreamNameUp$ overlap. The
overlap has the same selected StreamName window on both readings, so
\autoref{thm:realup-streamname-window-determinacy-boundary} identifies the
endpoint $\RatUp$ classifier rows, positive denominator witnesses, common
e-one tail readbacks, and dyadic source rows through the displayed $\hsame$
ledger.

Finally apply
\autoref{thm:realup-streamname-finite-window-ledger-boundary} on the overlap
itself. The only exported ledger rows are the selected unary observation, the
overlap $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the endpoint
denominator rows, and the dyadic source rows named by the finite-window
exhaustion boundary.

Since \autoref{thm:realup-scoped-certificate-boundary} admits no exported row
for host $\mathsf{Nat}$ indices, host functions, quotient witnesses, or
unrecorded infinite stream data, no further datum can distinguish the two
restricted readings on their common overlap.
\end{proof}

\begin{theorem}[RealUp finite-window two-step restriction coherence]
\label{thm:realup-finite-window-two-step-restriction-coherence}
Suppose a $\RealUp$ finite-window exhaustion package is exposed for a
$\StreamNameUp$ window $W$, and suppose $U$ is a certified $\StreamNameUp$
subwindow of $W$ while $V$ is a certified $\StreamNameUp$ subwindow of $U$. The
$\RealUp$ read surface obtained by restricting first from $W$ to $U$ and then
from $U$ to $V$ is the same public finite $\mathsf{BHist}$ surface as the direct
restriction from $W$ to $V$. Both readings expose the same
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readbacks,
$\mathsf{DyadicRatCore}$ source rows, $\hsame$ ledger, and
$\mathsf{RealLedgerPolicy}$ boundary.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:realup-finite-window-exhaustion-subwindow-closure} to the ambient
window $W$ and the certified subwindow $U$. This identifies the $U$ reading as
the inherited finite-window package whose public rows are exactly the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint denominator rows,
common e-one tail readbacks, and dyadic source rows of $W$ restricted to $U$.

Apply
\autoref{thm:realup-finite-window-exhaustion-subwindow-closure} again to the
$U$ package and the certified subwindow $V$. The two-step reading therefore has
only the inherited $V$ observation rows, the endpoint $\RatUp$ classifier rows,
positive denominator witnesses, common e-one tail readbacks, and
$\mathsf{DyadicRatCore}$ source rows already named by the ambient package.

For the direct $W$ to $V$ reading, use
\autoref{thm:realup-streamname-window-determinacy-boundary}. The selected
StreamName window and endpoint denominator rows for $V$ are the same in the
direct and two-step presentations, so the endpoint classifiers, denominator
witnesses, readbacks, and source rows are identified through the displayed
$\hsame$ ledger.

Finally apply
\autoref{thm:realup-streamname-finite-window-ledger-boundary} to the common
$V$ surface. The public finite $\mathsf{BHist}$ ledger is exactly the selected
observation, the $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
endpoint rows, the dyadic source rows, and the
$\mathsf{RealLedgerPolicy}$ boundary. Hence the two-step restriction and the
direct restriction expose the same $\RealUp$ read surface.
\end{proof}

\begin{theorem}[RealUp finite-window partition exactness]
\label{thm:realup-finite-window-partition-exactness}
Suppose a $\RealUp$ finite-window exhaustion package is exposed for a
$\StreamNameUp$ window $W$. Let $(W_i)_{i\in I}$ be a finite family of
certified $\StreamNameUp$ subwindows of $W$ such that every certified unary
observation row of $W$ is carried by at least one $W_i$, and such that every
pairwise intersection exposed by two selected subwindows is certified by the
overlap boundary of
\autoref{thm:realup-finite-window-exhaustion-overlap-closure}. Then the
$\RealUp$ read surface assembled from the finite family $(W_i)_{i\in I}$ is
the same public finite $\mathsf{BHist}$ surface as the direct read surface of
$W$. The two surfaces have the same
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readbacks,
$\mathsf{DyadicRatCore}$ source rows, $\hsame$ ledger, and
$\mathsf{RealLedgerPolicy}$ boundary.
\end{theorem}
\begin{proof}
Apply \autoref{thm:realup-finite-window-exhaustion-subwindow-closure} to each
certified subwindow $W_i$. Each local read therefore contains only the
inherited unary observation rows, finite-window classifier rows, endpoint
denominator rows, common e-one tail readbacks, and dyadic source rows coming
from the ambient window $W$.

On every certified overlap $W_i\cap W_j$, use
\autoref{thm:realup-finite-window-exhaustion-overlap-closure}. It identifies
duplicate observations and their endpoint $\RatUp$ classifier rows through the
same $\hsame$ ledger, so the finite family contributes one public observation
row for each certified observation of $W$ rather than a separate row for each
covering subwindow.

If a selected observation is reached through a smaller certified refinement,
\autoref{thm:realup-finite-window-two-step-restriction-coherence} identifies
the refined read with the direct restriction from $W$. Thus changing the
subwindow presentation does not change the visible read surface.

Finally repack the covered observation rows by
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. The coverage
hypothesis supplies every unary observation row of $W$, and the overlap and
two-step coherence rows remove duplicate presentations. The assembled surface
is therefore exactly the direct finite-window surface of $W$.
\end{proof}

\begin{theorem}[RealUp finite-window directed refinement seal]
\label{thm:realup-finite-window-directed-refinement-seal}
Suppose two $\RealUp$ finite-window exhaustion packages are exposed over the
same $\StreamNameUp$ source, with certified windows $W$ and $W'$. Suppose also
that there is a certified common refinement, given by a finite family of
$\StreamNameUp$ subwindows whose union covers every certified unary observation
row of both $W$ and $W'$, and whose pairwise overlaps satisfy
\autoref{thm:realup-finite-window-exhaustion-overlap-closure}. Then the two
finite-window presentations expose the same public $\mathsf{BHist}$ read
surface. In particular, they have the same
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readbacks,
$\mathsf{DyadicRatCore}$ source rows, $\hsame$ ledger, and
$\mathsf{RealLedgerPolicy}$ boundary, and neither presentation exports host
indices, quotient witnesses, or unrecorded infinite stream data.
\end{theorem}
\begin{proof}
Apply \autoref{thm:realup-finite-window-partition-exactness} to the window
$W$ and the certified common refinement. The coverage hypothesis says that the
refinement carries every certified unary observation row visible from $W$, so
the refinement assembly is the same public finite $\mathsf{BHist}$ surface as
the direct $W$ presentation.

Apply \autoref{thm:realup-finite-window-partition-exactness} again to the
window $W'$. The same refinement family covers every certified unary
observation row visible from $W'$, so the refinement assembly is also the same
public finite $\mathsf{BHist}$ surface as the direct $W'$ presentation.

It remains to compare the two uses of the refinement. When a refinement
subwindow is reached through either ambient window, use
\autoref{thm:realup-finite-window-two-step-restriction-coherence} to identify
the restricted read with the direct refinement read. On intersections between
two refinement subwindows, use
\autoref{thm:realup-finite-window-exhaustion-overlap-closure} to identify the
duplicate classifier rows, denominator witnesses, readbacks, and dyadic source
rows through the same $\hsame$ ledger.

Finally apply \autoref{thm:realup-streamname-finite-window-ledger-boundary} to
the common refinement surface. Its ledger contains exactly the selected
observation rows, endpoint $\RatUp$ rows, positive denominator witnesses,
common e-one tail readbacks, $\mathsf{DyadicRatCore}$ rows, and
$\mathsf{RealLedgerPolicy}$ boundary. Therefore both finite-window
presentations expose the same public surface, with no additional host index,
quotient, or infinite-stream datum available to distinguish them.
\end{proof}

\begin{definition}[RealUp finite-window refinement envelope]
\label{def:realup-finite-window-refinement-envelope}
A $\RealUp$ finite-window refinement envelope over one $\StreamNameUp$ source
is a finite $\mathsf{BHist}$ package whose rows consist of certified
$\StreamNameUp$ finite windows, a common-refinement package for every ordered
pair of carried windows, the overlap-closure witnesses for each refinement
family, the two-step restriction coherence witnesses for every displayed
subwindow chain, the endpoint $\RatUp$ classifier rows, the positive
denominator witnesses, the $\mathsf{DyadicRatCore}$ source rows, the shared
$\hsame$ ledger identifying duplicate presentations, and the
$\mathsf{RealLedgerPolicy}$ boundary. The envelope exports only these finite
rows and their $\mathsf{Pkg}$ provenance.
\end{definition}

\begin{theorem}[RealUp finite-window refinement envelope coherence]
\label{thm:realup-finite-window-refinement-envelope-coherence}
Let $E$ be a $\RealUp$ finite-window refinement envelope over a fixed
$\StreamNameUp$ source. If two certified windows $W$ and $W'$ are carried by
$E$, then the public read surface exposed from $W$ is the same finite
$\mathsf{BHist}$ read surface as the one exposed from $W'$. The common surface
contains exactly the envelope's
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, endpoint $\RatUp$
classifier rows, positive denominator witnesses, common e-one tail readbacks,
$\mathsf{DyadicRatCore}$ source rows, shared $\hsame$ ledger, and
$\mathsf{RealLedgerPolicy}$ boundary, with no host index, quotient witness, or
unrecorded infinite stream datum.
\end{theorem}
\begin{proof}
Choose the common-refinement package in $E$ for the ordered pair $(W,W')$.
The package supplies a finite family of certified subwindows covering every
certified unary observation row of both windows, together with the required
overlap-closure witnesses.

Apply
\autoref{thm:realup-finite-window-directed-refinement-seal} to this pair. The
seal reduces the comparison of the two ambient presentations to the public
surface assembled from their displayed common refinement.

The assembly through the common refinement is exact by
\autoref{thm:realup-finite-window-partition-exactness}. Whenever a row is
read through an intermediate refinement before reaching the displayed
subwindow, \autoref{thm:realup-finite-window-two-step-restriction-coherence}
identifies that reading with the direct restriction used by the refinement
surface.

Finally apply
\autoref{thm:realup-streamname-finite-window-ledger-boundary}. The only public
rows left in the envelope are the selected finite-window observation rows,
endpoint $\RatUp$ classifier rows, positive denominator witnesses, common
e-one tail readbacks, dyadic source rows, the shared $\hsame$ ledger, and the
$\mathsf{RealLedgerPolicy}$ boundary. Since that boundary has no slot for a
host index, quotient witness, or unrecorded infinite stream datum, the two
carried windows expose one public read surface.
\end{proof}

\begin{theorem}[RealUp finite-window refinement envelope consumer coverage]
\label{thm:realup-finite-window-refinement-envelope-consumer-coverage}
Let $E$ be a $\RealUp$ finite-window refinement envelope over a fixed
$\StreamNameUp$ source, and let $W$ be any certified window carried by $E$.
Every $\mathsf{RegSeqRat}$ handoff induced by $W$, and every finite-window
$\RealUp$ seal read induced by $W$, factors through exactly the rows carried
by $E$: the $\StreamNameUp$ finite-window classifier rows, the
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and $\mathsf{UnaryHistory}$ rows,
the pointwise $\mathsf{RatHistoryClassifier}$ rows, the endpoint denominator
rows, the $\mathsf{DyadicRatCore}$ source rows, the shared $\hsame$ ledger,
and the $\mathsf{RealLedgerPolicy}$ boundary. Conversely, any such row family
inside $E$ repacks into the same $\mathsf{RegSeqRat}$ handoff and
finite-window $\RealUp$ seal surface. No completion object, quotient witness,
host-index equality, or unrecorded stream datum is part of this consumer
surface.
\end{theorem}
\begin{proof}
First compare the chosen carried window with the envelope surface. Apply
\autoref{thm:realup-finite-window-refinement-envelope-coherence} with $W$ and
any other carried representative used by the consumer. The comparison
identifies the consumer-facing read with the envelope's finite public
$\mathsf{BHist}$ surface, so the read cannot escape the rows named in the
envelope.

Next expose the stream-name boundary. By
\autoref{thm:realup-streamname-finite-window-ledger-boundary}, a finite
window contributes only its classifier rows, the certified probe and unary
history rows, the endpoint denominator witnesses, the shared $\hsame$ ledger,
and the $\mathsf{RealLedgerPolicy}$ boundary. These are precisely rows already
stored in $E$.

For a $\mathsf{RegSeqRat}$ consumer, apply
\autoref{thm:streamname-regseqrat-pointwise-handoff}. Its pointwise handoff
uses the $\mathsf{RatHistoryClassifier}$ rows read from the same
$\StreamNameUp$ finite window. Then apply
\autoref{thm:regseqrat-finite-window-dyadic-source-exhaustion} to replace the
dyadic source requirements by the displayed $\mathsf{DyadicRatCore}$ source
rows and endpoint denominator rows carried by the envelope.

The reverse packing uses the same two displayed handoff theorems in the
opposite direction of construction: the finite-window classifier,
$\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, $\mathsf{UnaryHistory}$,
pointwise rational classifier, denominator, dyadic-source, $\hsame$, and
ledger-policy rows assemble the public consumer interface. Since all cited
boundaries are finite $\mathsf{BHist}$ rows, there is no constructor slot for
completion, quotient identification, host-index equality, or unrecorded
stream data.
\end{proof}

\input{parts/concrete_instances/real/stream_prefix/13_realup_finite_window_refinement_envelope_nonescape}
