\begin{theorem}[RealUp scoped finite-window read surface]
\label{thm:realup-scoped-finite-window-read-surface}
The selected finite $\RealUp$ observation windows read exactly the
carrier/classifier, stability/transport, finite ledger, dyadic source,
$\RegSeqRat$ spine, $\StreamNameUp$, $\RatUp$, $\mathsf{UnaryHistory}$,
$\hsame$, and $\mathsf{RealLedgerPolicy}$ rows named by
\autoref{thm:realup-scoped-certificate-boundary}. They read no quotient datum,
completion datum, metric-completeness certificate, arithmetic or order
operation, Classical datum, or standard-bridge datum.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealupScopedFiniteWindowReadSurface}
\begin{proof}
First collect the finite-window observation face. Apply
\autoref{thm:realup-finite-window-exhaustion-obligation}: every selected finite
$\RealUp$ window exposes the endpoint $\RatUp$ classifiers, unary denominator
rows, common e-one tail readback, and dyadic source rows consumed by the
$\RealUp$ seal.

Next identify the structural rows read by that observation field. Apply
\autoref{thm:real-stream-prefix-carrier-obligation} for the DyadicRatCore,
$\RegSeqRat$, $\StreamNameUp$, and $\RatUp$ carrier source. Apply
\autoref{thm:real-stream-prefix-classifier-obligation} for the constant-history
and unary stream classifier source. Apply
\autoref{thm:real-stream-prefix-stability-obligation} for pointwise $\hsame$
transport and selected-continuation stability.

Finally attach the ledger and certificate boundary. Apply
\autoref{thm:real-stream-prefix-ledger-seal-obligation} for the finite
$\mathsf{RealLedgerPolicy}$ rows and seal consumption. Then apply
\autoref{thm:realup-scoped-certificate-boundary}, which states that these rows
are exactly the scoped $\RealUp$ certificate boundary and excludes quotient,
completion, arithmetic, order, metric-completeness, Classical, and
standard-bridge data.
\end{proof}

\begin{theorem}[RealUp common finite-window pullback transitive restriction]
\label{thm:realup-common-window-pullback-transitive-restriction}
Let $W_0$ and $W_1$ be certified finite $\RealUp$ observation-window packages,
let $U$ be a certified common $\StreamNameUp$ subwindow of their displayed
$\mathsf{ProbeBundle}$ windows, and let $V$ be a certified $\StreamNameUp$
subwindow of $U$. Assume that the restrictions of $W_0$ and $W_1$ to $U$ carry
matching $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, matching
$\RegSeqRat$ spine rows, matching endpoint
$\mathsf{DyadicRatCoreObservationRow}$ witnesses, matching displayed $\hsame$
transports, matching $\Cont$ rows, matching $\Pkg$ provenance, and matching
finite $\mathsf{RealLedgerPolicy}$ rows. Then the two routes to $V$ expose the
same finite $\mathsf{BHist}$ packet and the same finite
$\mathsf{RealLedgerPolicy}$ row: restrict the direct common-window pullback from
$U$ to $V$, or first pull both $\RealUp$ packages back to $U$ and then restrict
that common packet to $V$.

This is a finite-window descent theorem only. It exposes no quotient,
completion, metric-completeness datum, global Cauchy modulus, arithmetic
operation, order operation, Classical representative, or standard bridge row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:realup-streamname-regseqrat-common-window-pullback} on the common
subwindow $U$. The hypotheses name the same StreamName classifier, regular
sequence spine, dyadic endpoint observations, endpoint transports, continuation
rows, package provenance, and finite real-ledger row, so the pullback over $U$
is a single finite $\mathsf{BHist}$ packet with a single
$\mathsf{RealLedgerPolicy}$ row.

Now compare the two restrictions from $U$ to $V$. Apply
\autoref{thm:realup-finite-window-two-step-restriction-coherence} to the
certified chain $W_i \supseteq U \supseteq V$ for each selected observation
window $W_i$. It identifies the direct restriction of the displayed
$W_i$ package to $V$ with the two-step restriction through $U$, with the same
finite packet, classifier rows, endpoint rows, transport ledger, provenance,
and real-ledger boundary.

Finally use
\autoref{thm:realup-streamname-regseqrat-uniform-window-readback} on the
endpoint window $V$. The StreamName-RegSeqRat handoff and the dyadic endpoint
rows are already matched after the two-step coherence comparison, so the
endpoint readback rows on $V$ and the finite $\mathsf{RealLedgerPolicy}$ row
are the same for both routes.
\end{proof}

\begin{theorem}[RealUp StreamName-RegSeqRat finite-window correspondence]
\label{thm:realup-streamname-regseqrat-window-correspondence}
A selected finite $\RealUp$ observation-window surface is equivalent, as BEDC
public data, to the pair consisting of the public $\StreamNameUp$ finite-window
interface of \autoref{thm:streamname-public-finite-window-interface} and the
$\RegSeqRat$ dyadic source exhaustion rows consumed in
\autoref{thm:realup-finite-window-exhaustion-obligation}. The pair records
exactly the finite-window stream classifier, endpoint $\RatUp$ classifiers,
unary denominator witnesses, common e-one tail readback, DyadicRatCore source
rows, $\mathsf{UnaryHistory}$ endpoints, $\hsame$ transport, and finite
$\mathsf{RealLedgerPolicy}$ ledger rows, and it records no quotient,
completion, arithmetic, order, metric-completeness, Classical, or
standard-bridge datum.
\end{theorem}
\begin{proof}
For the projection direction, first apply
\autoref{thm:realup-scoped-finite-window-read-surface}. It identifies the
selected finite $\RealUp$ read surface with the DyadicRatCore, $\RegSeqRat$,
$\StreamNameUp$, $\RatUp$, unary-history, $\hsame$, and finite ledger rows that
the scoped certificate exposes.

Then apply
\autoref{thm:realup-finite-window-export-through-streamname-interface}. The
$\StreamNameUp$ component factors through the public finite-window interface of
\autoref{thm:streamname-public-finite-window-interface}, and the remaining rows
are exactly the dyadic source, regular sequence, endpoint, unary, transport,
and ledger rows read by
\autoref{thm:realup-finite-window-exhaustion-obligation}.

For the reconstruction direction, start with the displayed pair. Repack the
$\StreamNameUp$ finite-window classifier rows through the public interface, and
repack the endpoint $\RatUp$ classifiers, unary denominator witnesses, common
e-one tail readback, and DyadicRatCore source rows through the exhaustion
obligation.

The two packets share the same finite $\mathsf{UnaryHistory}$ endpoints,
$\hsame$ transport, and $\mathsf{RealLedgerPolicy}$ readback. Combining those
shared rows gives precisely the scoped boundary named in
\autoref{thm:realup-scoped-finite-window-read-surface}, so the reconstructed
surface is the original selected finite $\RealUp$ observation-window surface
and contains no excluded datum.
\end{proof}

\begin{theorem}[RealUp finite-window export through StreamNameUp interface]
\label{thm:realup-finite-window-export-through-streamname-interface}
Every selected finite $\RealUp$ observation-window read surface of
\autoref{thm:realup-scoped-finite-window-read-surface} factors its
stream-name component through the public $\StreamNameUp$ finite-window interface
of \autoref{thm:streamname-public-finite-window-interface}. Its stream-name
component is exactly the $\mathsf{RatStreamNameFiniteWindowClassifier}$ surface
with classifier-to-window coverage, singleton-window exhaustion, reindexing and
point-map coverage, structural laws, the selected endpoint package, and
finite-window stability fields.

After this factorization, the remaining $\RealUp$ rows are only the
DyadicRatCore observation rows, $\RegSeqRat$ spine rows, $\RatUp$ endpoint rows,
$\mathsf{UnaryHistory}$, $\hsame$ transport, and
$\mathsf{RealLedgerPolicy}$. The exported finite-window surface contains no
quotient datum, completion datum, arithmetic or order operation,
metric-completeness certificate, Classical datum, or standard bridge.
\end{theorem}
\begin{proof}
First identify the public stream-name finite-window surface. Apply
\autoref{thm:streamname-public-finite-window-interface}: the
$\StreamNameUp$ component available to downstream $\RealUp$ windows is the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ surface together with
classifier-to-window coverage, singleton-window exhaustion, reindexing and
point-map coverage, structural laws, the selected endpoint package, and
finite-window stability fields.

Next identify the selected $\RealUp$ read surface. Apply
\autoref{thm:realup-scoped-finite-window-read-surface}; it says that selected
finite observation windows read the DyadicRatCore source, $\RegSeqRat$ spine,
$\StreamNameUp$ rows, $\RatUp$ endpoints, $\mathsf{UnaryHistory}$, $\hsame$
transport, and finite $\mathsf{RealLedgerPolicy}$ rows, while excluding quotient,
completion, arithmetic, order, metric-completeness, Classical, and
standard-bridge data.

The ten-field fit is: traditional target, finite $\RealUp$ observation export;
BEDC source, DyadicRatCore plus $\StreamNameUp$, $\RegSeqRat$, and $\RatUp$ over
$\mathsf{BHist}$; carrier, selected rational-observation windows; classifier,
finite-window pointwise $\RatUp$ classification; stability, $\StreamNameUp$
finite-window stability plus $\hsame$ transport; ledger, finite observation
index plus $\mathsf{RealLedgerPolicy}$; core theorem, this block; exactness,
factorization through the public finite-window interface; standard bridge, none;
status, proof target.

	Finally close directly at the finite-window surface. The $\StreamNameUp$
	component is exactly the public finite-window interface just identified, and
	\autoref{thm:realup-scoped-finite-window-read-surface} supplies the whole local
	read surface in which that component sits. Removing the $\StreamNameUp$ component
	therefore leaves precisely the DyadicRatCore observation rows, $\RegSeqRat$
	spine rows, $\RatUp$ endpoint rows, $\mathsf{UnaryHistory}$, $\hsame$ transport,
	and finite $\mathsf{RealLedgerPolicy}$ rows, with the excluded quotient,
	completion, arithmetic, order, metric-completeness, Classical, and
	standard-bridge data still absent.
	\end{proof}

\begin{theorem}[RealUp StreamName window stability consumption]
\label{thm:realup-streamname-window-stability-consumption}
Let $s,t,s',t'$ be rational observation maps carried by a finite
$\mathsf{ProbeBundle}$ window, and let the selected unary observation rows be
the endpoint rows read by the finite $\RealUp$ prefix surface. Suppose the
$\StreamNameUp$ finite-window classifier accepts the window for $(s,t)$,
suppose the packet carries bundled pointwise $\hsame$ transports from $(s,t)$
to $(s',t')$, and suppose the selected transported endpoint package of
\autoref{thm:rat-stream-name-finite-window-transported-selected-full-endpoint-package}
is present.

Then the transported selected $\RealUp$ prefix read surface has the same
finite $\mathsf{RealLedgerPolicy}$ boundary as in
\autoref{thm:realup-scoped-finite-window-read-surface}. It factors through
\autoref{thm:realup-finite-window-export-through-streamname-interface} as a
finite $\mathsf{BHist}$ read surface, with no quotient datum, completion datum,
metric-completeness certificate, Classical datum, or standard-bridge datum.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:rat-stream-name-finite-window-stability-fields} to the accepted
$\StreamNameUp$ classifier and the bundled pointwise $\hsame$ transports. This
produces the transported finite-window classifier for $(s',t')$ over the same
finite $\mathsf{ProbeBundle}$ boundary.

Next apply
\autoref{thm:rat-stream-name-finite-window-transported-selected-full-endpoint-package}
to the selected endpoint rows. The transported package supplies the positive
denominator rows, unary shape rows, zero-head exclusion rows, and one-tail
agreement rows needed by the selected endpoint surface.

Finally repack these transported rows through
\autoref{thm:realup-finite-window-export-through-streamname-interface}. The
scoped read surface of \autoref{thm:realup-scoped-finite-window-read-surface}
then supplies the unchanged finite $\mathsf{RealLedgerPolicy}$ boundary, so
the transported prefix surface is still a finite $\mathsf{BHist}$ interface
and none of the excluded quotient, completion, metric, Classical, or bridge
data is introduced.
\end{proof}

\begin{theorem}[RealUp StreamName source-exhaustion equivalence]
\label{thm:realup-streamname-source-exhaustion-equivalence}
For any selected finite $\RealUp$ observation window, the selected read surface
has exactly the $\StreamNameUp$ component supplied by
\autoref{thm:streamname-public-finite-window-interface} together with the
RegSeqRat and DyadicRatCore finite-window source rows consumed by
\autoref{thm:realup-finite-window-exhaustion-obligation}. Conversely, the
concrete RegSeqRat and DyadicRatCore rows, together with the public
$\StreamNameUp$ finite-window package, repack into the $\StreamNameUp$ component
of \autoref{thm:realup-scoped-finite-window-read-surface}.

This equivalence is internal to the selected finite $\mathsf{BHist}$ window. It
does not read a quotient datum, completion datum, metric-completeness
certificate, arithmetic or order operation, Classical datum, or standard-bridge
datum.
\end{theorem}
\begin{proof}
Project the selected $\RealUp$ read surface using
\autoref{thm:realup-scoped-finite-window-read-surface}. This gives the visible
$\StreamNameUp$ rows, the RegSeqRat spine rows, the DyadicRatCore source rows,
the $\RatUp$ endpoint rows, $\mathsf{UnaryHistory}$, $\hsame$ transport, and the
finite $\mathsf{RealLedgerPolicy}$ rows, with the excluded data absent.

Next apply \autoref{thm:realup-finite-window-export-through-streamname-interface}
to the projected stream-name component. It identifies that component with the
public $\mathsf{RatStreamNameFiniteWindowClassifier}$ package of
\autoref{thm:streamname-public-finite-window-interface}.

The remaining finite source rows are read from
\autoref{thm:realup-finite-window-exhaustion-obligation}: DyadicRatCore supplies
the selected dyadic observation rows, and RegSeqRat supplies the spine rows used
by the finite window. These rows are concrete $\mathsf{BHist}$ entries rather
than quotient or completion witnesses.

For the converse direction, start with the public $\StreamNameUp$ finite-window
package and the concrete RegSeqRat and DyadicRatCore rows just described. The
public package reconstructs the same selected stream-name component, while the
source rows provide exactly the surrounding finite-window inputs required by
\autoref{thm:realup-scoped-finite-window-read-surface}. Repacking these rows
therefore recovers the selected $\StreamNameUp$ component inside the same
$\RealUp$ read surface, and no excluded datum is introduced.
\end{proof}

\begin{theorem}[RealUp finite-window constant-stream seal factorization]
\label{thm:realup-finite-window-constant-stream-seal-factorization}
Let $d,e:\Hist$ and let $W$ be a certified finite $\mathsf{ProbeBundle}$ window.
Consider selected finite $\RealUp$ observation rows whose $\StreamNameUp$
component is generated by the constant rational streams
$\mathsf{RatConstStream}_d$ and $\mathsf{RatConstStream}_e$. A displayed
$\mathsf{RatHistoryClassifier}(d,e)$ together with the constant stream-name
package factors the selected read surface through
\autoref{thm:streamname-public-finite-window-interface}. After this
factorization the remaining visible rows are exactly the DyadicRatCore
observation rows, RegSeqRat spine rows, $\RatUp$ endpoint rows,
$\mathsf{UnaryHistory}$ rows, $\hsame$ transport rows, and finite
$\mathsf{RealLedgerPolicy}$ rows recorded by the selected $\RealUp$ window.

Conversely, those DyadicRatCore, RegSeqRat, $\RatUp$, unary-history,
$\hsame$, and finite $\mathsf{RealLedgerPolicy}$ rows, together with the
constant stream-name package for
$\mathsf{RatHistoryClassifier}(d,e)$, repack into the selected finite
$\RealUp$ read surface. The factorization contains no quotient row, completion
row, metric-completeness certificate, Classical datum, or standard-bridge
datum.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:rat-stream-name-constant-bridge-package-exactness}. It converts
the displayed $\mathsf{RatHistoryClassifier}(d,e)$ into the constant
stream-name package for $\mathsf{RatConstStream}_d$ and
$\mathsf{RatConstStream}_e$ without replacing the histories by a quotient or
standard model.

Next restrict this package to the finite window $W$ by
\autoref{thm:rat-stream-name-constant-finite-window-exactness}. The resulting
finite constant-stream rows are exactly the rows accepted by the public
$\StreamNameUp$ finite-window interface of
\autoref{thm:streamname-public-finite-window-interface}.

Apply
\autoref{thm:realup-finite-window-export-through-streamname-interface} to the
selected $\RealUp$ observation window. Its stream-name component therefore
factors through the public interface, while
\autoref{thm:realup-streamname-source-exhaustion-equivalence} identifies the
unconsumed finite source rows as precisely the DyadicRatCore observations,
RegSeqRat spine, $\RatUp$ endpoints, unary-history rows, $\hsame$ transports,
and finite $\mathsf{RealLedgerPolicy}$ rows.

For the converse direction, start with this same finite list of remaining
rows and the constant stream-name package. The public interface reconstructs
the selected $\StreamNameUp$ component, and the source-exhaustion equivalence
supplies exactly the surrounding RegSeqRat, DyadicRatCore, $\RatUp$,
unary-history, transport, and ledger rows needed by the scoped $\RealUp$ read
surface. Repacking these displayed rows recovers the selected finite surface,
again without quotient, completion, metric-completeness, Classical, or
standard-bridge data.
\end{proof}

\begin{theorem}[StreamName Real seal factorization diamond]
\label{thm:streamname-real-seal-factorization-diamond}
Let $W \subseteq W'$ be finite public $\StreamNameUp$ rational observation
windows with displayed prefix refinement. Suppose the windows carry accepted
$\RegSeqRat$ spine rows, a shared DyadicRatCore endpoint ledger,
$\mathsf{ProbeBundle}$ and $\mathsf{InBundle}$ rows, $\mathsf{UnaryHistory}$
rows, a finite $\Cont$ ledger, displayed $\hsame$ endpoint transports, and
$\mathsf{Pkg}$ provenance. Then restricting the $W'$ $\RealUp$ seal
factorization to $W$ and factoring the $W$ seal read through the
StreamName--$\RegSeqRat$ source produce the same visible $\mathsf{BHist}$
source tuple.

That tuple is exactly the StreamName finite-window row, accepted
$\RegSeqRat$ seal row, dyadic endpoint rows, bundle rows, unary-history rows,
finite continuation rows, displayed endpoint transports, and provenance rows.
It contains no completion row, quotient representative, host index equality,
Classical choice row, metric-completeness datum, or standard-bridge datum.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:streamname-real-seal-factorization-refinement-stability} to the
displayed inclusion $W \subseteq W'$. It identifies the restricted larger
factorization with the direct smaller-window factorization over the same
bundle, history, transport, continuation, and provenance rows.

Next use
\autoref{thm:streamname-regseqrat-realup-seal-source-determinacy}. The two
routes have the same public StreamName row, accepted $\RegSeqRat$ spine,
dyadic endpoint ledger, bundle membership, unary observations, $\Cont$ ledger,
$\hsame$ endpoint transports, and $\Pkg$ provenance, so their visible seal
source is fixed to one $\mathsf{BHist}$ tuple.

Finally, \autoref{thm:streamname-regseqrat-realup-seal-source-minimality}
rules out any additional source row beyond that tuple, and
\autoref{thm:realup-finite-window-constant-stream-seal-factorization} repacks
it as the selected finite $\RealUp$ seal surface, without adding completion,
quotient, host-equality, Classical, metric-completeness, or standard-bridge
data.
\end{proof}

\begin{theorem}[RealUp finite-window StreamName readback package]
\label{thm:realup-finite-window-streamname-readback-package}
Let $W$ be a certified finite $\mathsf{ProbeBundle}$ window and let a public
$\RealUp$ finite-window classifier read be accepted over a $\StreamNameUp$
source. Then there is a displayed $\mathsf{BHist}$ packet whose rows are exactly
the unary schedule for $W$, the $\RatUp$ observation endpoints visible in the
window, the $\StreamNameUp$ finite-window classifier row, the $\RealUp$ scoped
window row, the $\Cont$ and $\hsame$ transport ledger connecting the stream
read to the real read, and the $\Pkg$ provenance of the selected source rows.
Every public $\RealUp$ finite-window classifier read through this
$\StreamNameUp$ source factors through that packet.

The packet contains no quotient row, completion row, metric-completeness
certificate, global Cauchy modulus, arithmetic or order operation, Classical
datum, or standard bridge. Its endpoint reads are exactly the displayed
$\RatUp$ observations and its classifier reads are exactly the displayed
$\StreamNameUp$ and scoped $\RealUp$ finite-window rows.
\end{theorem}
\begin{proof}
Begin with the accepted finite-window $\RealUp$ read and project its
$\StreamNameUp$ component. By
\autoref{thm:realup-finite-window-export-through-streamname-interface}, this
component factors through the public $\StreamNameUp$ finite-window interface,
so the stream-name classifier row is displayed as a finite $\mathsf{BHist}$
row rather than as an ambient stream equality.

Next use
\autoref{thm:realup-streamname-window-stability-consumption}. It transports
the projected stream-name row across the selected finite window and records
the required $\Cont$ and $\hsame$ ledger entries. These entries are the only
transport rows consumed by the scoped $\RealUp$ classifier read.

For constant rational endpoints, apply
\autoref{thm:realup-finite-window-constant-stream-seal-factorization}. It
identifies the endpoint part of the read with the displayed $\RatUp$
observation rows, the unary schedule, and the surrounding finite
$\mathsf{RealLedgerPolicy}$ rows. For non-constant accepted stream-name
sources, the same packet shape is obtained by reading the $\RatUp$ endpoints
already exposed by the finite StreamName window.

Finally apply
\autoref{thm:realup-finite-window-common-refinement-determinacy}. Any two
displayed packets supporting the same public $\RealUp$ classifier read admit
the same common finite refinement, hence determine the same visible rows up
to the recorded $\hsame$ transports. This gives the announced readback packet
and shows that every public finite-window classifier read factors through it.
\end{proof}

\begin{theorem}[RealUp empty-window StreamName boundary]
\label{thm:realup-empty-window-streamname-boundary}
Let $W$ be a selected finite $\RealUp$ observation window whose
$\mathsf{ProbeBundle}$ boundary is empty. Then the $\StreamNameUp$ component of
the $\RealUp$ finite-window readback package is exactly the public empty-window
vacuity row of \autoref{thm:streamname-public-empty-window-vacuity}. After this
identification, the remaining visible $\RealUp$ rows are only the scoped ledger,
dyadic source, $\mathsf{UnaryHistory}$, $\hsame$, and
$\mathsf{RealLedgerPolicy}$ rows already listed by
\autoref{thm:realup-scoped-finite-window-read-surface}.

The empty-window read contains no quotient row, completion row,
metric-completeness certificate, Classical datum, arithmetic or order row, or
standard-bridge datum.
\end{theorem}
\begin{proof}
Project the selected finite readback through
\autoref{thm:realup-finite-window-streamname-readback-package}. The projected
$\StreamNameUp$ row is a displayed finite-window classifier row inside the same
$\mathsf{BHist}$ packet as the unary schedule, endpoint rows, $\Cont$ and
$\hsame$ transport ledger, and $\Pkg$ provenance.

Apply \autoref{thm:realup-finite-window-export-through-streamname-interface} to
factor that stream-name row through the public finite-window interface. Since
the $\mathsf{ProbeBundle}$ boundary of $W$ is empty, the corresponding public
stream-name row is the empty-window vacuity row of
\autoref{thm:streamname-public-empty-window-vacuity}.

It remains to identify what the $\RealUp$ packet still exposes. The scoped read
surface theorem \autoref{thm:realup-scoped-finite-window-read-surface} lists
exactly the surviving finite rows: the scoped ledger, dyadic source,
$\mathsf{UnaryHistory}$, $\hsame$, and $\mathsf{RealLedgerPolicy}$ entries. The
same theorem excludes quotient, completion, metric-completeness, Classical,
arithmetic, order, and standard-bridge data, and the empty-window projection
does not add any of them.
\end{proof}

\begin{theorem}[RealUp StreamName-RegSeqRat tail-selector determinacy]
\label{thm:realup-streamname-regseqrat-tail-selector-determinacy}
Let $W_0$ and $W_1$ be selected finite $\RealUp$ observation-window packages.
Assume that they display the same public $\StreamNameUp$ finite-window
classifier row, the same $\RegSeqRat$ spine rows, the same DyadicRatCore
observation rows, matching $\RatUp$ endpoint classifiers, and the same finite
$\Cont/\hsame$ ledger. Then every selected tail-classifier readback extracted
from $W_0$ and every selected tail-classifier readback extracted from $W_1$
represent the same finite $\RealUp$ tail read up to the displayed $\hsame$
transport. Moreover the two packages expose the same
$\mathsf{RealLedgerPolicy}$ row.

The conclusion is scoped to the selected finite-window surface. It does not
assert equality of quotient completions, metric completions, arithmetic
operations, order operations, Classical representatives, or standard bridge
data.
\end{theorem}
\begin{proof}
Project both selected packages through
\autoref{thm:realup-finite-window-streamname-readback-package}. Each projection
has a $\StreamNameUp$ component, $\RegSeqRat$ spine rows, DyadicRatCore
observation rows, $\RatUp$ endpoint classifiers, a finite $\Cont/\hsame$ ledger,
and a surrounding $\mathsf{RealLedgerPolicy}$ row.

Identify the shared $\StreamNameUp$ component by
\autoref{thm:realup-streamname-source-exhaustion-equivalence}. Under the
hypotheses, the two finite-window classifier rows consume the same concrete
stream-name source and the same regular-sequence and dyadic observation rows.

The constant and empty boundary theorems remove non-displayed choices. Apply
\autoref{thm:realup-finite-window-constant-stream-seal-factorization} to the
constant endpoint case and
\autoref{thm:realup-empty-window-streamname-boundary} to the empty-window case.
In both cases the visible tail read is forced by the selected endpoint,
stream-name, regular-sequence, dyadic, and ledger rows already present in the
projected package.

It remains to compare the two selected tail reads. Compose the displayed
$\hsame$ transports in the common finite ledger. Since the two packages have the
same $\Cont/\hsame$ ledger and the same $\mathsf{RealLedgerPolicy}$ boundary,
the transported tail classifiers coincide up to $\hsame$, and the exposed
$\mathsf{RealLedgerPolicy}$ rows are identical as public finite-window rows.
\end{proof}

\begin{theorem}[RealUp finite-window StreamName readback uniformity]
\label{thm:realup-finite-window-streamname-readback-uniformity}
Let $W$ be a certified finite $\mathsf{ProbeBundle}$ window supporting a public
$\RealUp$ finite-window readback through a $\StreamNameUp$ source, and let
$U$ be either a certified finite subwindow of $W$ or a certified finite common
refinement of two such windows. Assume that the restriction to $U$ carries the
same public $\StreamNameUp$ finite-window row, the same $\RegSeqRat$ spine rows,
the same DyadicRatCore observation rows, and the restricted $\Cont/\hsame$
ledger displayed over $U$. Then the $\RealUp$ readback packet over $W$
restricts over $U$ to the same visible $\RatUp$ endpoint rows and to the same
finite $\mathsf{RealLedgerPolicy}$ row.

Equivalently, certified passage to a displayed finite subwindow or common
finite refinement preserves the public endpoint readback and the real-ledger
row determined by the StreamName-RegSeqRat-DyadicRatCore surface. The assertion
does not identify quotient completions, metric completions, global Cauchy
moduli, arithmetic operations, order operations, Classical representatives, or
standard bridge data.
\end{theorem}
\begin{proof}
Start with the selected $\RealUp$ read over $W$ and apply
\autoref{thm:realup-finite-window-streamname-readback-package}. This displays a
single finite $\mathsf{BHist}$ packet containing the public $\StreamNameUp$
finite-window row, the $\RegSeqRat$ spine, the DyadicRatCore observations, the
visible $\RatUp$ endpoints, the restricted $\Cont/\hsame$ ledger, the
$\Pkg$ provenance, and the finite $\mathsf{RealLedgerPolicy}$ row.

Restrict this displayed packet along the certified subwindow $U$, or along the
certified common refinement when two windows are present. The common-refinement
determinacy theorem
\autoref{thm:realup-finite-window-common-refinement-determinacy} says that any
two displayed packets with the same public rows over the refinement determine
the same finite surface up to the recorded $\hsame$ transports.

The source rows remaining after restriction are exactly the public stream-name
row, the regular-sequence spine, and the dyadic observation rows named in the
hypotheses. This is the source-exhaustion equivalence of
\autoref{thm:realup-streamname-source-exhaustion-equivalence}, while
\autoref{thm:streamname-public-finite-window-interface} identifies the
restricted stream-name row as the same public finite-window interface row
rather than an ambient stream equality.

With the stream-name source and the restricted transport ledger fixed, the
readback package has no remaining displayed choice for the $\RatUp$ endpoints
or for the finite $\mathsf{RealLedgerPolicy}$ row. Hence the packet over $W$
restricts to the same visible endpoint rows and the same real-ledger row over
$U$.
\end{proof}

\begin{theorem}[RealUp StreamName-RegSeqRat uniform window readback]
\label{thm:realup-streamname-regseqrat-uniform-window-readback}
Let $W_0$ and $W_1$ be certified finite $\RealUp$ observation-window packages,
and let $U$ be a certified finite common refinement of their selected
$\mathsf{ProbeBundle}$ windows. Assume that both packages factor through the
public $\StreamNameUp$ finite-window interface, that their restrictions to $U$
carry the same $\StreamNameUp$ classifier row, and that the displayed
$\RegSeqRat$ pointwise seal gives the same regular-sequence spine over the
same $\mathsf{BHist}$ endpoints, $\hsame$ transports, $\Cont$ rows, and
$\Pkg$ provenance rows. Then the two restricted $\RealUp$ readback packets have
the same visible $\RatUp$ endpoint readback rows on every selected finite
subwindow of $U$, and they expose the same finite
$\mathsf{RealLedgerPolicy}$ row.

The statement is only a finite-window consumer theorem. It identifies the rows
read through the StreamName-RegSeqRat handoff and does not identify quotient
completions, metric completions, global Cauchy moduli, arithmetic operations,
order operations, Classical representatives, or standard bridge data.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal}. The common
$\StreamNameUp$ classifier row over $U$ and the displayed $\RegSeqRat$
pointwise seal determine a single finite-window handoff surface, with the
$\mathsf{BHist}$ endpoints, $\hsame$ transports, $\Cont$ rows, and $\Pkg$
provenance rows kept in the public packet.

Next compare that handoff surface with the selected $\RealUp$ read surface.
Apply \autoref{thm:realup-streamname-regseqrat-window-correspondence}. It
identifies the $\RealUp$ finite-window observation surface with the pair
consisting of the public $\StreamNameUp$ finite-window interface and the
$\RegSeqRat$ dyadic source exhaustion rows, together with the same endpoint,
transport, provenance, and finite-ledger rows.

Finally restrict along each selected finite subwindow of $U$. The hypotheses
now match the input of
\autoref{thm:realup-finite-window-streamname-readback-uniformity}: the public
stream-name row, regular-sequence spine, dyadic observation rows, and
restricted $\Cont/\hsame$ ledger are the same. Therefore the two consumer
packets read back the same visible $\RatUp$ endpoint rows on each selected
finite window and expose the same finite $\mathsf{RealLedgerPolicy}$ row.
\end{proof}

\begin{theorem}[RealUp common finite-window pullback]
\label{thm:realup-streamname-regseqrat-common-window-pullback}
Let $W_0$ and $W_1$ be certified finite $\RealUp$ observation-window packages,
and let $U$ be a certified common $\StreamNameUp$ subwindow of their displayed
$\mathsf{ProbeBundle}$ windows. Assume that the restrictions to $U$ carry the
same $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the same
$\RegSeqRat$ spine rows, and endpoint
$\mathsf{DyadicRatCoreObservationRow}$ witnesses matched by the displayed
$\hsame$ transports. Assume also that the two selected
$\RealUp$ read surfaces expose their endpoint rows through the same restricted
$\mathsf{BHist}$ packet and the same finite $\Cont/\Pkg$ provenance ledger over
$U$. Then the restricted $\RealUp$ readback packets over $U$ are the same
finite $\mathsf{BHist}$ packet and expose the same finite
$\mathsf{RealLedgerPolicy}$ row.

The theorem identifies only the finite StreamNameUp-RegSeqRat-DyadicRatCore
window shared by the two read surfaces. It does not export quotient
completions, metric completions, global Cauchy moduli, arithmetic operations,
order operations, Classical representatives, or standard bridge data.
\end{theorem}
\begin{proof}
Restrict both certified observation windows to the common subwindow $U$. The
restricted surfaces still carry exactly the displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, $\RegSeqRat$ spine rows,
DyadicRatCore endpoint witnesses, $\hsame$ transports, $\Cont$ rows, and
$\Pkg$ provenance named in the hypotheses.

Apply the finite-window source-exhaustion obligation of
\autoref{thm:realup-streamname-source-exhaustion-equivalence} to the endpoint
rows. It says that, over the selected finite packet, no endpoint readback row
remains outside the StreamNameUp-RegSeqRat-DyadicRatCore source family.

Next apply
\autoref{thm:realup-streamname-regseqrat-uniform-window-readback}. The matching
stream-name classifier rows and regular-sequence spine rows identify the
StreamName-RegSeqRat handoff over $U$, while the dyadic endpoint witnesses and
the displayed $\hsame$ transports fix the endpoint side of the handoff.

Finally use the ledger exactness of the selected $\RealUp$ read surface, as in
\autoref{thm:realup-finite-window-streamname-readback-package}. The only
visible finite packet left over $U$ is the shared $\mathsf{BHist}$ packet, and
the only finite ledger row exposed by that packet is the same
$\mathsf{RealLedgerPolicy}$ row.
\end{proof}

\begin{theorem}[RealUp StreamName RegSeqRat cover seal associativity]
\label{thm:realup-streamname-regseqrat-cover-seal-associativity}
Let $K_0$, $K_1$, and $K_2$ be certified finite $\RealUp$ observation windows
with certified $\StreamNameUp$ finite-window restrictions
$K_0\leftarrow K_1\leftarrow K_2$. Assume that the displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the induced $\RegSeqRat$
seal rows, and the finite $\Cont/\hsame/\Pkg$ ledgers are composable over these
two restrictions. Then the $\RealUp$ finite-window seal obtained by first
pulling the displayed $\mathsf{BHist}$ seal surface back from $K_2$ to $K_1$ and
then from $K_1$ to $K_0$ is the same displayed $\mathsf{BHist}$ seal surface as
the direct pullback from $K_2$ to $K_0$.

The statement uses only the displayed $\StreamNameUp$, $\RegSeqRat$, $\RealUp$,
$\mathsf{BHist}$, $\hsame$, $\Cont$, and finite-window ledger rows. It includes
no completion, quotient, metric-completeness, Classical, arithmetic, order, or
standard bridge datum.
\end{theorem}
\begin{proof}
Apply \autoref{thm:realup-streamname-regseqrat-common-window-pullback} to the
restriction $K_2\to K_1$ and then to the restriction $K_1\to K_0$. The two
applications identify the intermediate seal with displayed
$\StreamNameUp$ classifier rows, $\RegSeqRat$ spine rows, endpoint witnesses,
and the finite $\Cont/\hsame/\Pkg$ ledger on $K_1$ and $K_0$.

Apply the same common-window pullback theorem directly to the composed
restriction $K_2\to K_0$. Its input rows are exactly the rows obtained by
composing the two certified restrictions: the same StreamName finite-window
classifier, the same induced RegSeqRat seal rows, and the same finite transport
ledger displayed over $K_0$.

The common-refinement determinacy theorem
\autoref{thm:realup-finite-window-common-refinement-determinacy} compares the
two displayed packets over the common finite window $K_0$. Since their
StreamName, RegSeqRat, endpoint, transport, and provenance rows agree, the
visible $\RealUp$ seal surface is unique up to the recorded $\hsame$ transports.

Finally use the tail-reindexing stability of
\autoref{thm:streamname-regseqrat-tail-reindexing-stability}. It says that the
tail rows introduced by the nested restriction are the same pointwise rows as
those introduced by the composed restriction. Thus the two pullback routes
display the same finite $\mathsf{BHist}$ seal surface and the same finite
ledger rows.
\end{proof}

\begin{theorem}[RealUp StreamName RegSeqRat cover identity seal]
\label{thm:realup-streamname-regseqrat-cover-identity-seal}
Let $K$ be a certified finite $\RealUp$ observation window carrying the
displayed $\StreamNameUp$ finite-window, $\RegSeqRat$, and
DyadicRatCore seal rows exposed by
\autoref{thm:realup-finite-window-streamname-readback-package}. Restrict this
displayed seal along the identity certified subwindow $K\leftarrow K$. Then the
restricted surface is the same finite $\mathsf{BHist}$ seal surface, with the
same $\hsame/\Cont/\Pkg$ provenance ledger and the same finite
$\mathsf{RealLedgerPolicy}$ row.

The identity restriction exports no quotient, completion, metric-completeness,
Classical representative, arithmetic operation, order operation, or standard
bridge datum. It only records that the finite
StreamNameUp-RegSeqRat-DyadicRatCore read surface is neutral under the
certified identity subwindow.
\end{theorem}
\begin{proof}
Start with the finite readback package of
\autoref{thm:realup-finite-window-streamname-readback-package}. It displays the
$\StreamNameUp$ finite-window classifier, the $\RegSeqRat$ spine rows, the
DyadicRatCore endpoint rows, and the finite $\hsame/\Cont/\Pkg$ ledger on $K$.

Apply \autoref{thm:realup-streamname-regseqrat-common-window-pullback} to the
identity certified subwindow $K\leftarrow K$. The source and target windows
are the same certified window, so the pullback reads exactly the same
classifier rows, endpoint witnesses, provenance rows, and
$\mathsf{RealLedgerPolicy}$ entry.

Finally view the identity restriction as the neutral member of the composition
law in \autoref{thm:realup-streamname-regseqrat-cover-seal-associativity}. A
pullback followed by the identity subwindow, or preceded by it, has the same
direct route. Thus the displayed $\mathsf{BHist}$ seal surface and its finite
ledger are unchanged.
\end{proof}

\begin{theorem}[RealUp window refinement cover pullback exhaustion]
\label{thm:realup-window-refinement-cover-pullback-exhaustion}
Let $W$ be a certified finite $\RealUp$ observation window. Let
$\mathcal{C}_0$ and $\mathcal{C}_1$ be two finite $\StreamNameUp$ cover
presentations of the displayed window of $W$, and let $\mathcal{R}$ be a
certified finite common refinement whose restrictions to the two covers carry
the same $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the same
$\RegSeqRat$ spine rows, the same DyadicRatCore observation witnesses, and the
same displayed $\hsame$ transports. Assume that every cover member exposes its
$\RatUp$ endpoint rows through the displayed finite $\mathsf{BHist}$ packet
and through the same restricted $\Cont/\Pkg$ provenance ledger. Then the
$\RealUp$ read surface assembled from $\mathcal{C}_0$, the $\RealUp$ read
surface assembled from $\mathcal{C}_1$, and the direct read surface of $W$
expose exactly the same finite $\mathsf{BHist}$ packet.

The common packet consists of the $\StreamNameUp$ classifier rows, the
$\RegSeqRat$ spine, the DyadicRatCore observation rows, the visible
$\RatUp$ endpoint rows, the displayed $\hsame/\Cont/\Pkg$ provenance rows, and
the finite $\mathsf{RealLedgerPolicy}$ row. The result does not export quotient
completions, metric completions, global Cauchy moduli, arithmetic operations,
order operations, Classical representatives, or standard bridge data.
\end{theorem}
\begin{proof}
Pull both cover presentations back to the certified common refinement
$\mathcal{R}$. By
\autoref{thm:realup-streamname-regseqrat-common-window-pullback}, the
restrictions of the two cover-assembled surfaces to each member of
$\mathcal{R}$ display the same classifier rows, $\RegSeqRat$ spine rows,
DyadicRatCore observation witnesses, $\RatUp$ endpoint rows, and
$\hsame/\Cont/\Pkg$ provenance rows.

Assemble those refined packets back along each cover. The cover-seal
associativity theorem
\autoref{thm:realup-streamname-regseqrat-cover-seal-associativity} says that
refining through $\mathcal{R}$ and then returning along $\mathcal{C}_i$ gives
the same displayed finite $\mathsf{BHist}$ surface as the direct pullback along
that cover. Thus the two assembled cover surfaces expose the same refined
packet.

Compare each assembled cover with the direct read surface of $W$. The identity
seal theorem
\autoref{thm:realup-streamname-regseqrat-cover-identity-seal} identifies the
direct surface with the neutral cover presentation on the same certified finite
window, so associativity transports the refined packet from either cover route
to the direct route.

It remains only to check that no visible row is left outside this packet.
Apply the source-exhaustion equivalence
\autoref{thm:realup-streamname-source-exhaustion-equivalence} to the
StreamNameUp-RegSeqRat-DyadicRatCore source rows, and then apply the
finite-window ledger boundary recorded in
\autoref{thm:realup-finite-window-streamname-readback-package}. The endpoint,
transport, provenance, and $\mathsf{RealLedgerPolicy}$ rows are therefore
exactly the shared finite $\mathsf{BHist}$ packet named in the statement.
\end{proof}

\begin{theorem}[RealUp StreamName-RegSeqRat directed-window consumer surface]
\label{thm:realup-streamname-regseqrat-directed-window-consumer-surface}
Let $\mathcal{D}$ be a finite directed system of certified $\RealUp$
observation windows. Assume that every transition map in $\mathcal{D}$ is the
displayed $\StreamNameUp$ finite-window restriction, and that every endpoint
row agrees under the $\RegSeqRat$ finite-window seal. Then the whole directed
system exposes one unique consumer-visible $\mathsf{BHist}$ packet.

That packet consists exactly of the $\StreamNameUp$ classifier rows, the
$\RegSeqRat$ spine rows, the DyadicRatCore observation rows, the visible
$\RatUp$ endpoint rows, the displayed $\hsame/\Cont/\Pkg$ provenance rows, and
the finite $\mathsf{RealLedgerPolicy}$ row. It exports no quotient completion,
metric completeness, global Cauchy modulus, order operation, or standard bridge
datum.
\end{theorem}
\begin{proof}
First choose any finite cofinal window of the directed system. Apply
\autoref{thm:streamname-regseqrat-uniform-finite-window-seal} to place the
endpoint rows under the common $\RegSeqRat$ finite-window seal, and apply
\autoref{thm:streamname-regseqrat-reindexed-window-structural-closure} to
transport the same rows along the displayed $\StreamNameUp$ restrictions.

Next compare any two routes through the chosen directed window. The cover-seal
associativity theorem
\autoref{thm:realup-streamname-regseqrat-cover-seal-associativity} identifies
the iterated restriction with the direct restriction, so the classifier,
spine, endpoint, and provenance rows do not depend on the route.

Finally apply
\autoref{thm:realup-window-refinement-cover-pullback-exhaustion} to the finite
family of windows generated by the chosen routes. It says that every cover
presentation, every common refinement, and the direct read surface expose the
same finite $\mathsf{BHist}$ packet. The source list in that theorem is
exactly the consumer surface named here, so no quotient completion, metric
completeness, global Cauchy modulus, order operation, or standard bridge datum
is added.
\end{proof}
