\begin{theorem}[RealUp terminal refinement seal boundary]
\label{thm:realup-terminal-refinement-seal-boundary}
Let $E$ be a $\RealUp$ finite-window refinement envelope over a fixed
$\StreamNameUp$ source. Suppose two refined finite-window presentations
$W$ and $W'$ are carried by $E$, are connected by the directed-refinement seal
of \autoref{thm:realup-finite-window-directed-refinement-seal}, and are then
read by a terminal finite-window $\RealUp$ seal consumer. Then every terminal
consumer of either presentation reads exactly the same finite source
boundary:
\begin{enumerate}
  \item the $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows;
  \item the bundled $\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows;
  \item the pointwise $\mathsf{RatHistoryClassifier}$ rows;
  \item the accepted $\RegSeqRat$ finite-window spine;
  \item the $\mathsf{DyadicRatCore}$ source rows;
  \item the visible $\Cont$, $\hsame$, $\Pkg$, and
  $\mathsf{RealLedgerPolicy}$ ledger rows.
\end{enumerate}
No terminal read exposes a quotient row, completion object, host
$\mathsf{Nat}$ index, host function, $\mathsf{Classical}$ datum,
metric-completeness certificate, arithmetic row, order row, or standard bridge
row.
\end{theorem}
\begin{proof}
First identify both refined presentations with the same envelope boundary.
Apply
\autoref{thm:realup-finite-window-refinement-envelope-coherence} to the two
windows carried by $E$. The result gives one public finite $\mathsf{BHist}$
surface containing exactly the envelope classifier, endpoint, dyadic-source,
$\hsame$, and ledger-policy rows.

Next use the directed-refinement seal. The comparison row supplied by
\autoref{thm:realup-finite-window-directed-refinement-seal} forces the
presentation read from $W$ and the presentation read from $W'$ through that
same finite refinement surface. Thus the two refined windows have no distinct
source boundary for a later consumer to inspect.

Now pass this common finite-window surface to the terminal seal consumer.
Apply \autoref{thm:streamname-realup-terminal-seal-boundary}. It reads the
finite StreamName-to-RegSeqRat packet as the selected classifier rows, bundled
unary and membership rows, pointwise rational classifier rows, endpoint and
denominator rows, the accepted RegSeqRat spine, the dyadic source rows, and
the finite $\Cont$ and $\hsame$ transport ledger.

Finally apply \autoref{thm:streamname-realup-terminal-seal-scope-readback}.
The scope readback keeps the source $\Pkg$ rows and
$\mathsf{RealLedgerPolicy}$ boundary attached to the same packet and excludes
all rows outside it. Hence no terminal consumer can read quotient data,
completion data, host indices, host functions, $\mathsf{Classical}$ data,
metric-completeness certificates, arithmetic or order rows, or standard
bridge rows.
\end{proof}

\begin{theorem}[RealUp directed-refinement terminality]
\label{thm:realup-streamname-regseqrat-directed-refinement-terminality}
Let $\mathcal F$ be a directed finite family of StreamName tail-window
coverage packets over the same public $\StreamNameUp$ endpoints and the same
accepted $\RegSeqRat$ finite-window spine. Then the directed common-refinement
packet obtained from $\mathcal F$ is terminal for finite $\RealUp$ consumers:
every finite $\RealUp$ consumer whose source reads one member of
$\mathcal F$ factors through this common-refinement packet.

For any selected subwindow, restriction from the common-refinement packet
recovers the same $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
same $\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the same pointwise
$\mathsf{RatHistoryClassifier}$ rows, the same accepted $\RegSeqRat$ spine,
the same $\mathsf{DyadicRatCore}$ endpoint rows, and the same visible
$\Cont$, $\hsame$, $\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows as the
original StreamName finite-window packet.

The terminal factorization introduces no completion object, quotient row,
host-index equality, metric-completeness row, arithmetic or order operation,
or standard bridge row.
\end{theorem}
\begin{proof}
First form the common packet. Apply
\autoref{thm:streamname-tail-window-cover-common-refinement} to any two
members of the directed family; directedness supplies a family member whose
selected observation window contains both restrictions, so the generated
packet has the same public endpoints and accepted $\RegSeqRat$ spine.

For more than two selected windows, iterate the same construction along the
finite family. Apply
\autoref{thm:streamname-tail-window-refinement-associativity} at each regrouping
step. The resulting packet is independent of the parenthesization, and every
selected subwindow restricts back to the same StreamName classifier,
unary-history, bundle-membership, pointwise rational-history, accepted spine,
dyadic endpoint, continuation, history, package, and ledger-policy rows.

Next pass a finite $\RealUp$ consumer through the packet boundary. Apply
\autoref{thm:streamname-tail-window-terminal-consumer-factorization}. Every
consumer row factors through the displayed tail-window ledger, and equality of
the displayed packet gives equality of the finite read surface.

Finally compare this terminal read with the $\RealUp$ seal boundary. Apply
\autoref{thm:realup-terminal-refinement-seal-boundary}. The terminal consumer
therefore reads exactly the rows recovered by the selected subwindow
restriction and no object outside that finite surface. In particular, the
construction adds no completion object, quotient row, host-index equality,
metric-completeness row, arithmetic or order operation, or standard bridge
row.
\end{proof}

\begin{theorem}[StreamName Real-RegSeq terminal source uniqueness]
\label{thm:streamname-real-regseq-terminal-source-uniqueness}
Let $C$ be a public $\StreamNameUp$ finite-window package. Suppose two
terminal finite-window $\RealUp$ seal consumers are reached from $C$ and that
their displayed $\RegSeqRat$ handoff rows expose the same source data:
\begin{enumerate}
  \item the $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows;
  \item the $\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows;
  \item the pointwise $\mathsf{RatHistoryClassifier}$ rows;
  \item the accepted $\RegSeqRat$ spine;
  \item the $\mathsf{DyadicRatCore}$ rows; and
  \item the visible $\Cont$, $\hsame$, $\Pkg$, and
  $\mathsf{RealLedgerPolicy}$ rows.
\end{enumerate}
Then the two terminal consumers have the same source-boundary projection.
Conversely, equality of the terminal source-boundary projection is exactly
equality of the rows listed above.

The projection contains no quotient row, completion object, host index, host
function, $\mathsf{Classical}$ datum, metric-completeness row, arithmetic or
order row, or standard bridge row.
\end{theorem}
\begin{proof}
Begin with the two routes from the public $\StreamNameUp$ package $C$ to the
terminal finite-window consumers. By
\autoref{thm:streamname-common-refinement-terminal-route-determinacy}, route
choice cannot change the finite StreamName source packet read at the terminal
interface.

Next identify the packet read by the terminal $\RealUp$ seal. Apply
\autoref{thm:realup-terminal-regseqrat-source-coverage}. The terminal source
surface is precisely the displayed StreamName classifier, unary-history,
membership, pointwise rational-history, accepted RegSeqRat spine, dyadic-core,
transport, package, and real-ledger rows.

For uniqueness of the accepted spine, use
\autoref{thm:regseqrat-tail-classifier-pullback-uniqueness}. Any two terminal
candidates compatible with those displayed rows factor through the same
selected $\RegSeqRat$ source surface, so the source-boundary projection is
forced to agree.

For the converse, apply
\autoref{thm:streamname-regseqrat-pointwise-handoff}. Equality of the
source-boundary projection reads back exactly the StreamName finite-window
classifier rows, the unary and membership rows, the pointwise rational
classifier rows, the accepted RegSeqRat spine, the dyadic-core rows, and the
visible $\Cont$, $\hsame$, $\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows.

The coverage theorem also gives the exclusion clause. Since the projection is
the finite RegSeqRat source surface and nothing outside it, no quotient row,
completion object, host index, host function, $\mathsf{Classical}$ datum,
metric-completeness row, arithmetic or order row, or bridge row can be
recovered from the terminal consumer.
\end{proof}

\begin{theorem}[StreamName common-refinement terminal route determinacy]
\label{thm:streamname-common-refinement-terminal-route-determinacy}
Let $C$ be a certified $\StreamNameUp$ common-refinement package. Suppose two
finite-window $\RealUp$ terminal seal consumers are reached from $C$ by
choosing possibly different common-refinement routes, then passing through the
same StreamName finite-window restriction and $\RegSeqRat$ handoff interface.
Then the two terminal reads expose the same source tuple:
\begin{enumerate}
  \item the restricted
  $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows;
  \item the common $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and
  $\mathsf{UnaryHistory}$ rows;
  \item the pointwise $\mathsf{RatHistoryClassifier}$ rows;
  \item the accepted $\RegSeqRat$ spine selected by those rows;
  \item the displayed dyadic endpoint rows; and
  \item the displayed $\hsame$, $\Cont$, and $\Pkg$ provenance rows.
\end{enumerate}
The terminal tuple contains no quotient row, completion object, host-index
equality, metric-completeness datum, or additional $\RealUp$ seal classifier
outside the packet just listed.
\end{theorem}
\begin{proof}
Start with the certified common-refinement package $C$. Apply
\autoref{thm:streamname-common-refinement-source-confluence}. The two routes
therefore determine the same StreamName source packet and the same displayed
common-refinement provenance rows.

Next restrict that packet to the terminal finite window. By
\autoref{thm:streamname-tail-window-cover-common-refinement}, both route reads
use the same finite-window classifier rows, the same $\mathsf{ProbeBundle}$ and
$\mathsf{InBundle}$ entries, and the same unary-history window.

Now apply \autoref{thm:streamname-regseqrat-pointwise-handoff}. The restricted
StreamName packet hands off to one pointwise rational-history packet, one
accepted $\RegSeqRat$ spine, and the same dyadic endpoint rows, with the
displayed $\hsame$, $\Cont$, and $\Pkg$ provenance carried along unchanged.

Finally use \autoref{thm:realup-terminal-regseqrat-source-coverage}. A terminal
finite-window $\RealUp$ seal consumer reads exactly that RegSeqRat source
surface and no larger host structure. Since both routes feed the same packet
into this coverage theorem, the two terminal reads expose the same listed
source tuple and exclude quotient rows, completion objects, host-index
equalities, metric-completeness data, and any extra $\RealUp$ seal classifier.
\end{proof}

\begin{theorem}[StreamName public window prefix determinacy]
\label{thm:streamname-public-window-prefix-determinacy}
Let $s,t : \mathsf{BHist}\to\mathsf{BHist}$ be StreamName rows, and let $B'$
and $B$ be probe windows. Suppose every certified $\UnaryHistory$ observation
in $B'$ is carried by $B$. Then every $\RegSeqRat$ terminal consumer, and every
finite-window $\RealUp$ terminal seal consumer, that reads
$\mathsf{RatStreamNameFiniteWindowClassifier}(s,t,B)$ through the public
$\StreamNameUp$ interface has the same terminal BEDC readback after restriction
to $B'$ as the consumer obtained by reading the certified prefix window
$B'$ directly.

The common restricted readback consists exactly of the pointwise $\RatUp$
observation rows, the $\mathsf{InBundle}$ witnesses, the $\hsame$ transports,
the $\Cont$ routes, and the $\mathsf{Pkg}$ provenance rows exposed by the
public StreamName interface on $B'$. If two restricted terminal routes have the
same endpoint package, then their finite BEDC readbacks are identical.

This determinacy statement exports no $\RegSeqRat$ regularity row, no
$\RealUp$ seal classifier beyond the restricted terminal source surface, no
quotient row, no host-index equality, and no completion data.
\end{theorem}
\begin{proof}
First read the larger public finite-window package. Apply
\autoref{thm:streamname-public-finite-window-interface}. It exposes only the
finite classifier rows, certified unary-history observations, membership
witnesses, pointwise rational observation rows, and visible transport and
provenance rows over $B$.

Next restrict that public packet to the certified prefix window. By
\autoref{thm:streamname-finite-window-restriction-export}, every
$\UnaryHistory$ observation carried by $B'$ has the same restricted classifier,
membership witness, $\hsame$ transport, $\Cont$ route, and $\mathsf{Pkg}$
provenance as its row inside $B$.

Now pass the restricted packet through the consumer-facing handoff. Apply
\autoref{thm:streamname-regseqrat-pointwise-handoff}. The $\RegSeqRat$ read and
the terminal finite-window $\RealUp$ read both see the same pointwise $\RatUp$
observation rows and the same restricted provenance rows from $B'$.

Finally use the terminal source comparison theorems. The source uniqueness
statement
\autoref{thm:streamname-real-regseq-terminal-source-uniqueness} identifies any
two terminal source projections with the same restricted row inventory, and
\autoref{thm:streamname-common-refinement-terminal-route-determinacy} removes
the choice of terminal route. Thus two restricted terminal routes with the same
endpoint package have the same finite BEDC readback, while all regularity,
seal-classifier, quotient, host-index, and completion data remain outside the
public prefix surface.
\end{proof}

\begin{theorem}[RealUp terminal RegSeqRat source coverage]
\label{thm:realup-terminal-regseqrat-source-coverage}
Every terminal finite-window $\RealUp$ seal consumer factors through exactly
one $\RegSeqRat$ source surface. That source surface consists of the displayed
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine, the
DyadicRatCore observation rows, and the visible $\Cont$, $\hsame$, $\Pkg$, and
$\mathsf{RealLedgerPolicy}$ ledger rows.

Conversely, any packet carrying exactly those rows repacks into the terminal
source surface read by the seal consumer. The coverage contains no quotient
row, completion object, host index, host function, $\mathsf{Classical}$ datum,
metric-completeness row, arithmetic or order row, or standard bridge row.
\end{theorem}
\begin{proof}
Start from the terminal read inventory of
\autoref{thm:realup-terminal-refinement-seal-boundary}. It lists precisely the
finite classifier, unary-history, membership, pointwise rational, accepted
spine, dyadic-source, transport, package, and ledger rows visible to a terminal
seal consumer.

For the source side, apply the finite-window StreamName-to-RegSeqRat handoff
from \autoref{thm:realup-streamname-regseqrat-window-correspondence}
and \autoref{thm:regseqrat-seal-finite-window-source-coverage}. These identify
the StreamName finite-window classifiers and dyadic observation rows as the
same source packet consumed by the $\RegSeqRat$ seal.

Now use the tail-classifier exactness package. By
\autoref{thm:regseqrat-tail-classifier-exactness} and
\autoref{thm:regseqrat-tail-classifier-normal-form-tail-coverage}, the
accepted $\RegSeqRat$ spine is the selected tail-classifier row determined by
the displayed StreamName, dyadic, endpoint-transport, package, and
$\mathsf{RealLedgerPolicy}$ data.

It remains to check uniqueness and repacking. Apply
\autoref{thm:regseqrat-tail-classifier-pullback-uniqueness}: any terminal
candidate compatible with the displayed rows factors through the same selected
$\RegSeqRat$ source surface. Conversely, carrying those rows supplies every
entry in the inventory above, so the packet repacks into the terminal seal
source surface and leaves all excluded quotient, completion, host, Classical,
metric, arithmetic, order, and bridge rows unread.
\end{proof}

\begin{theorem}[RealUp terminal RegSeqRat source minimality]
\label{thm:realup-terminal-regseqrat-source-minimality}
Every terminal finite-window $\RealUp$ seal consumer factors through a minimal
$\mathsf{BHist}$ source surface. That surface consists exactly of the displayed
$\StreamNameUp$ finite-window classifier rows, unary-history membership rows,
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, the $\mathsf{DyadicRatCore}$ rows, the endpoint transport rows, and the
visible $\Cont$ and $\mathsf{Pkg}$ ledger rows.

Removing any one of those row classes prevents repacking into the terminal
source surface read by the $\RealUp$ seal consumer. The minimal surface contains
no quotient row, completion object, host-index equality,
metric-completeness datum, or separate seal classifier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:realup-terminal-regseqrat-source-coverage}. Its coverage
direction gives the listed $\RegSeqRat$ source surface as the entire read
boundary of any terminal finite-window $\RealUp$ seal consumer, and its
converse direction repacks exactly packets carrying those rows.

Uniqueness of the selected source packet is supplied by
\autoref{thm:streamname-real-regseq-terminal-source-uniqueness}. A second
candidate surface with the same StreamName finite-window classifier,
unary-history, rational-history, accepted-spine, dyadic, transport, and ledger
rows is therefore the same terminal source packet.

Route independence is supplied by
\autoref{thm:streamname-common-refinement-terminal-route-determinacy}. Before a
terminal seal consumer reads the packet, every common-refinement route has
already fixed the same finite-window classifier rows, membership rows,
pointwise rational-history rows, accepted $\RegSeqRat$ spine, and dyadic
endpoint data.

Minimality follows by constructor and projection inversion on that packet.
Omitting a StreamName classifier row removes the finite-window route; omitting a
membership or unary-history row removes the window boundary; omitting a
pointwise rational-history row removes the rational observation; omitting the
accepted spine removes the $\RegSeqRat$ source; omitting a dyadic or endpoint
transport row removes the endpoint witness; and omitting a visible $\Cont$ or
$\mathsf{Pkg}$ row removes the ledger needed for repacking.

The same inversion shows that no further row can be required. The coverage and
determinacy theorems expose no quotient, completion object, host-index equality,
metric-completeness datum, or separate terminal seal classifier, so there is no
constructor or projection from which such data could be read.
\end{proof}

\begin{theorem}[RealUp DyadicRatCore StreamName RegSeqRat observation triangle]
\label{thm:dyadicratcore-streamname-regseqrat-observation-triangle}
For a terminal finite-window $\RealUp$ seal consumer, the
$\DyadicRatCoreUp$ public readback envelope, the public $\StreamNameUp$
finite-window classifier surface, and the $\RegSeqRat$ finite-window seal
source surface determine the same finite source packet and are mutually
recoverable.

The common packet consists exactly of the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine, the
$\mathsf{DyadicRatCore}$ observation rows, the endpoint transport rows, the
visible $\Cont$ and $\Pkg$ provenance rows, and the
$\mathsf{RealLedgerPolicy}$ rows. It contains no quotient row, completion
object, host $\mathsf{Nat}$ index, $\mathsf{Classical}$ datum,
metric-completeness row, arithmetic or order row, or standard bridge row.
\end{theorem}
\begin{proof}
First read the dyadic side. Apply
\autoref{thm:dyadicratcore-public-readback-envelope}. Its envelope exposes
exactly the dyadic observation rows and endpoint transport rows available to
the terminal packet, with no quotient or completion object attached.

Next read the finite stream-name side. Apply
\autoref{thm:streamname-public-finite-window-interface}. The public
finite-window classifier surface supplies the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, and the pointwise
$\mathsf{RatHistoryClassifier}$ rows on the same displayed finite window.

Now read the seal source side. Apply
\autoref{thm:regseqrat-seal-finite-window-source-coverage}. The
$\RegSeqRat$ seal source reads the accepted spine together with the same
finite-window classifier, unary-history, membership, pointwise rational,
dyadic observation, endpoint transport, $\Cont$, $\Pkg$, and ledger rows.

Finally apply \autoref{thm:realup-terminal-regseqrat-source-coverage} and
\autoref{thm:realup-terminal-regseqrat-source-minimality}. Coverage repacks
any packet carrying exactly those rows as the terminal source surface, while
minimality prevents an additional row class from being part of that terminal
source. Hence each of the three projections recovers the same finite source
packet, and the excluded quotient, completion, host-index, Classical, metric,
arithmetic, order, and bridge rows remain unread.
\end{proof}

\begin{theorem}[RealUp dyadic StreamName observation-triangle consumer]
\label{thm:realup-dyadic-streamname-observation-triangle-consumer}
Let $R$ be a terminal finite-window $\RealUp$ seal consumer whose source side
factors through the triangle of
\autoref{thm:dyadicratcore-streamname-regseqrat-observation-triangle}. Then
$R$ exposes exactly the common packet listed there: the
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine, the
$\mathsf{DyadicRatCore}$ observation rows, endpoint transport rows, visible
$\Cont$, $\hsame$, $\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows.

If two such consumer reads agree on the $\StreamNameUp$ finite-window
restriction and on the $\RegSeqRat$ handoff interface, then they expose the
same $\mathsf{DyadicRatCore}$ endpoint rows, $\Cont$, $\hsame$, $\Pkg$, and
$\mathsf{RealLedgerPolicy}$ rows. No quotient row, host index, completion
datum, arithmetic/order row, or standard bridge row is part of that
consumer-facing source packet.
\end{theorem}
\begin{proof}
Apply
\autoref{thm:dyadicratcore-streamname-regseqrat-observation-triangle}. The
factoring hypothesis places the consumer source on the triangle's common
packet, so its dyadic readback, finite StreamName restriction, and
$\RegSeqRat$ handoff are all projections of the same displayed source surface.

Apply \autoref{thm:realup-terminal-regseqrat-source-coverage} and
\autoref{thm:realup-terminal-regseqrat-source-minimality}. Coverage repacks the
listed rows as a terminal finite-window $\RealUp$ source, while minimality says
that no further source row can be demanded by such a consumer.

For two reads, use
\autoref{thm:realup-terminal-common-refinement-splice-uniqueness}. Agreement on
the StreamName finite-window restriction and the $\RegSeqRat$ handoff fixes the
common-refinement splice, hence fixes the DyadicRatCore endpoint rows and the
visible $\Cont$, $\hsame$, $\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows.

The excluded data have no projection from any of these three inputs. Quotient
rows, host indices, completion data, arithmetic/order rows, and standard bridge
rows are absent from the triangle packet and remain absent after terminal
source coverage and splice uniqueness are applied.
\end{proof}

\begin{theorem}[RealUp terminal common-refinement splice uniqueness]
\label{thm:realup-terminal-common-refinement-splice-uniqueness}
Let $C$ be a certified $\StreamNameUp$ common-refinement packet whose displayed
source tuple consists of a fixed $\StreamNameUp$ source name, a fixed accepted
$\RegSeqRat$ finite-window spine, and fixed $\mathsf{DyadicRatCore}$ source
rows. Suppose two terminal finite-window $\RealUp$ seal consumers are reached
from $C$ through possibly different common-refinement splices. If both splices
use the same StreamName finite-window restriction and the same $\RegSeqRat$
handoff interface, then the two terminal consumers expose the same finite
tuple:
\begin{enumerate}
  \item the $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows;
  \item the $\mathsf{ProbeBundle}$, $\mathsf{InBundle}$, and
  $\mathsf{UnaryHistory}$ rows;
  \item the pointwise $\mathsf{RatHistoryClassifier}$ rows;
  \item the accepted $\RegSeqRat$ spine;
  \item the $\mathsf{DyadicRatCore}$ observation rows; and
  \item the visible $\Cont$, $\hsame$, $\Pkg$, and
  $\mathsf{RealLedgerPolicy}$ rows.
\end{enumerate}
This uniqueness statement is only about that terminal source tuple. It does
not identify or expose quotient rows, host $\mathsf{Nat}$ indices, host
functions, $\mathsf{Classical}$ data, metric-completeness rows,
arithmetic/order rows, or standard bridge rows.
\end{theorem}
\begin{proof}
First compare the two splice routes before the terminal consumer reads them.
Apply
\autoref{thm:streamname-common-refinement-terminal-route-determinacy}. The
possibly different common-refinement routes through $C$ determine one terminal
StreamName source packet, one restricted finite-window classifier, one bundled
probe and unary-history packet, one pointwise rational-history packet, one
accepted $\RegSeqRat$ spine, and one displayed dyadic source surface.

Next pass that route-confluent packet through the terminal $\RealUp$ seal.
Apply \autoref{thm:realup-terminal-regseqrat-source-coverage}. The terminal
consumer factors through exactly the listed $\RegSeqRat$ source surface, and
any packet carrying exactly those rows repacks into the same terminal source
surface.

Both consumers therefore have the same displayed source tuple as their entire
terminal read boundary. Since the coverage theorem also excludes all rows
outside that packet, the uniqueness conclusion contains no quotient row, host
index, host function, $\mathsf{Classical}$ datum, metric-completeness row,
arithmetic or order row, or standard bridge row.
\end{proof}

\begin{theorem}[RealUp finite-window seal cofinality]
\label{thm:realup-finite-window-seal-cofinality}
Let $\mathcal{F}$ be a finite directed family of terminal finite-window
$\RealUp$ seal consumers over the same $\StreamNameUp$ source. Suppose
$\mathcal{F}$ has a cofinal common-refinement read $C$, and suppose the displayed
$\RegSeqRatUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows of every member of $\mathcal{F}$ agree with the corresponding
rows read from $C$. Then every member of $\mathcal{F}$ and the cofinal read $C$
determine the same terminal finite-window $\RealUp$ seal source surface.

The determined source surface consists only of the finite $\StreamNameUp$
restriction, the accepted $\RegSeqRat$ spine, the $\DyadicRatCore$ observation
rows, and the displayed $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance rows. It exports no quotient stream, host-index equality,
metric-completion datum, $\RealUp$ completeness row, or additional seal
classifier.
\end{theorem}
\begin{proof}
First use
\autoref{thm:realup-streamname-regseqrat-directed-refinement-terminality}.
Directed terminality
turns the finite family into a single terminal comparison against the cofinal
common-refinement read $C$, so each member is read through the same terminal
source route.

Next apply \autoref{thm:realup-terminal-regseqrat-source-coverage}. The cofinal
read and every family member factor through the displayed $\RegSeqRatUp$,
$\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows.
Apply \autoref{thm:realup-terminal-regseqrat-source-minimality} to remove every
row not present in that finite source inventory.

It remains to identify the member reads with the cofinal read. For each member,
apply \autoref{thm:realup-terminal-common-refinement-splice-uniqueness} to the
splice through $C$. The assumed agreement of the displayed rows fixes the
terminal splice, hence fixes the terminal source surface.

The last paragraph gives the stated boundary: the four cited theorems only
project the finite StreamName, RegSeqRat, DyadicRatCore, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ rows. There is no constructor in this route that
exports quotient streams, host-index equalities, metric-completion data,
$\RealUp$ completeness rows, or a further seal classifier.
\end{proof}

\begin{theorem}[RegSeqRat terminal tail-refinement seal]
\label{thm:regseqrat-terminal-tail-refinement-seal}
Let $S$ be a terminal $\StreamNameUp$ finite-window source and let $T$ be a
$\RegSeqRat$ stream whose finite-window reads factor through the terminal
$\RealUp$ source surface determined by $S$. For every certified tail
refinement $C$ of $T$ over the same public $\mathsf{BHist}$ window, there is a
unique terminal finite-window seal for $C$.

This seal is determined exactly by the terminal $\StreamNameUp$ source name,
the restricted $\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$ spine, the
$\DyadicRatCoreUp$ observation rows, and the visible $\hsame$, $\Cont$,
$\Pkg$, $\NameCert$, and $\mathsf{RealLedgerPolicy}$ rows. It is invariant
under $\hsame$ transport of the displayed history rows and under
$\Cont$-splicing along the certified common-refinement route. Its ledger is the
one inherited from the terminal $\StreamNameUp$ source packet, not an
independent $\RegSeqRat$ or $\RealUp$ ledger.

The terminal seal exposes no quotient stream, host-index equality, host
function, $\mathsf{Classical}$ datum, metric-completion object, arithmetic or
order row, standard bridge row, or separate tail-refinement classifier.
\end{theorem}
\begin{proof}
First identify the source from which the tail refinement can be read. Apply
\autoref{thm:streamname-real-regseq-terminal-source-uniqueness} and
\autoref{thm:realup-terminal-regseqrat-source-coverage}. The factoring
hypothesis places every finite window of $T$ on the terminal source packet
selected by $S$, and the coverage theorem repacks exactly those displayed rows
as the terminal $\RealUp$ source surface.

Next compare the certified refinement route with the terminal source route.
Apply \autoref{thm:streamname-common-refinement-terminal-route-determinacy}.
The common-refinement certificate fixes the same terminal StreamName source
name, the same restricted classifier rows, the same unary-history and
membership rows, the same pointwise rational-history rows, and the same
accepted $\RegSeqRat$ spine before the terminal seal is read.

Now splice the route into the terminal $\RealUp$ consumer. Apply
\autoref{thm:realup-terminal-common-refinement-splice-uniqueness}. Agreement
on the StreamName restriction and on the $\RegSeqRat$ handoff fixes the
$\DyadicRatCoreUp$ observation rows together with the visible $\hsame$,
$\Cont$, $\Pkg$, $\NameCert$, and $\mathsf{RealLedgerPolicy}$ rows. Therefore
transporting the displayed history data by $\hsame$ or changing only the
$\Cont$-splice representative cannot produce a second terminal seal.

Finally apply \autoref{thm:realup-finite-window-seal-cofinality}. Cofinality
collapses every certified tail-window refinement of $T$ to the same terminal
finite-window source surface. Since the only ledger rows in that surface are
the rows already read from the terminal $\StreamNameUp$ source packet, the seal
inherits that ledger and has no constructor that could export quotient,
completion, host, arithmetic, order, bridge, or separate classifier data.
\end{proof}

\begin{theorem}[RealUp terminal tail-refinement family factorization]
\label{thm:realup-terminal-tail-refinement-family-factorization}
Let $S$ be a terminal $\StreamNameUp$ finite-window source, let $T$ be an
accepted $\RegSeqRat$ packet over $S$, and let
$C_1,\ldots,C_n$ be a finite family of certified tail refinements of $T$ over
the same public $\mathsf{BHist}$ window. Suppose the family admits a cofinal
certified common refinement $C_\ast$ and that all displayed $\RegSeqRatUp$,
$\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and
$\mathsf{RealLedgerPolicy}$ rows agree after reading along $C_\ast$.

Then every terminal finite-window $\RealUp$ seal for a member $C_i$ factors
through the single cofinal source surface determined by $C_\ast$. This source
surface consists exactly of the finite $\StreamNameUp$ restriction, the
accepted $\RegSeqRat$ spine, the $\DyadicRatCore$ observation rows, and the
displayed provenance rows $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and
$\mathsf{RealLedgerPolicy}$.

The factorization exports no quotient stream, host-index equality, host
function, $\mathsf{Classical}$ datum, metric-completion object, arithmetic or
order row, standard bridge row, or separate tail-refinement classifier.
\end{theorem}
\begin{proof}
For each family member $C_i$, apply
\autoref{thm:regseqrat-terminal-tail-refinement-seal}. The seal theorem says
that the terminal finite-window seal for $C_i$ is read from the terminal
$\StreamNameUp$ source restriction, the accepted $\RegSeqRat$ spine, the
$\DyadicRatCoreUp$ observation rows, and the visible transport, package,
certificate, and ledger rows.

Now use the cofinal certificate $C_\ast$. Apply
\autoref{thm:realup-finite-window-seal-cofinality} to the finite family
$C_1,\ldots,C_n$. Cofinality replaces the separate member reads by the single
terminal read through $C_\ast$, so every member seal has the same finite
source surface once the displayed rows have been transported to the cofinal
refinement.

It remains to identify the splice rows on that common read. Apply
\autoref{thm:realup-terminal-common-refinement-splice-uniqueness}. The assumed
agreement of the $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$,
$\Pkg$, $\NameCert$, and $\mathsf{RealLedgerPolicy}$ rows fixes the terminal
splice over $C_\ast$, hence fixes the factor through the common source
surface.

The boundary clause follows from the same three cited results: their
constructors expose only the finite StreamName restriction, the accepted
RegSeqRat spine, the dyadic observation rows, and the displayed provenance
rows. None of them constructs quotient, host, classical, completion,
arithmetic, order, bridge, or separate classifier data.
\end{proof}

\begin{theorem}[RealUp common-refinement seal pullback]
\label{thm:streamname-realup-common-refinement-seal-pullback}
Let $C$ be a certified $\StreamNameUp$ common-refinement package, and let
$R$ and $R'$ be finite-window $\RealUp$ terminal seal consumers reached from
$C$ through compatible accepted $\RegSeqRat$ tail-refinement seals. Then
equality of the common-refinement source tuple is equivalent to equality of the
visible terminal seal boundary.

The common-refinement source tuple consists exactly of the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the $\mathsf{UnaryHistory}$
rows, the $\mathsf{ProbeBundle}$ rows, the $\mathsf{InBundle}$ rows, the
pointwise $\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRat$
spine, the $\mathsf{DyadicRatCore}$ endpoint rows, the visible $\Cont$,
$\hsame$, $\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows, and the certified
$\StreamNameUp$ provenance route in $C$.

The visible terminal seal boundary consists of the same finite
$\mathsf{BHist}$ ledger rows after the terminal $\RealUp$ consumer read. It
contains no completion object, quotient row, host index, metric-completeness
datum, arithmetic row, order row, or standard bridge row.
\end{theorem}
\begin{proof}
First assume equality of the common-refinement source tuple. Apply
\autoref{thm:streamname-common-refinement-terminal-route-determinacy} to the
two routes out of $C$. The route comparison identifies the restricted
StreamName classifier rows, probe and unary-history rows, bundle membership,
pointwise rational-history rows, accepted $\RegSeqRat$ spine, dyadic endpoint
rows, and visible transport and provenance rows before either terminal
consumer reads the packet.

Next pass the identified source tuple through the terminal $\RealUp$ surface.
Apply \autoref{thm:realup-terminal-regseqrat-source-coverage} and
\autoref{thm:regseqrat-terminal-tail-refinement-seal}. Coverage says that the
terminal consumer can read only the listed finite source rows, and the
tail-refinement seal says that compatible accepted $\RegSeqRat$ refinements
produce the unique terminal seal over those rows. Thus $R$ and $R'$ expose the
same visible terminal seal boundary.

Conversely assume equality of the visible terminal seal boundary. Apply
\autoref{thm:streamname-real-regseq-terminal-source-uniqueness}. Equality of
the terminal boundary reads back exactly the StreamName classifier rows,
unary-history and bundle rows, pointwise rational-history rows, accepted
$\RegSeqRat$ spine, dyadic endpoint rows, and visible $\Cont$, $\hsame$,
$\Pkg$, and $\mathsf{RealLedgerPolicy}$ rows.

It remains to identify the common-refinement route itself. Apply
\autoref{thm:realup-finite-window-seal-cofinality}. The two compatible
tail-refinement seals are cofinal over the same certified package $C$, so the
finite terminal boundary readback recovers the same common-refinement source
tuple. The cited coverage and seal theorems expose no completion, quotient,
host, metric, arithmetic, order, or bridge rows, so equality cannot depend on
any data outside that tuple.
\end{proof}

\begin{theorem}[RealUp terminal refinement-family pullback exhaustion]
\label{thm:realup-terminal-refinement-family-pullback-exhaustion}
Let $C_1,\ldots,C_n$ be a finite family of certified $\StreamNameUp$
tail-window coverage packets over the same public $\StreamNameUp$ endpoints
and the same accepted $\RegSeqRatUp$ spine. Assume that each pair
$C_i,C_j$ admits the common-refinement seal pullback of
\autoref{thm:streamname-realup-common-refinement-seal-pullback}. Then every
terminal $\RealUp$ finite-window consumer reached from the family factors
through one finite family pullback surface.

The family pullback surface exposes exactly the restricted
$\mathsf{RatStreamNameFiniteWindowClassifier}$ rows, the
$\mathsf{UnaryHistory}$ and $\mathsf{InBundle}$ rows, the pointwise
$\mathsf{RatHistoryClassifier}$ rows, the accepted $\RegSeqRatUp$ spine, the
$\DyadicRatCoreUp$ endpoint rows, the visible $\Cont$, $\hsame$, and
$\Pkg$ rows, and the $\mathsf{RealLedgerPolicy}$ rows. It exposes no
completion object, quotient row, host index, host function,
metric-completeness datum, arithmetic or order row, or standard bridge row.
\end{theorem}
\begin{proof}
Induct on the finite family. The empty and singleton cases are the terminal
finite-window surfaces supplied by
\autoref{thm:realup-streamname-regseqrat-directed-refinement-terminality};
there is then no nontrivial pairwise splice to compare.

For the induction step, suppose the first $k$ packets already factor through a
single displayed pullback surface and add $C_{k+1}$. Apply
\autoref{thm:streamname-common-refinement-terminal-route-determinacy} to make
the route from the accumulated surface to $C_{k+1}$ independent of the chosen
member route through the public endpoints and accepted $\RegSeqRatUp$ spine.

Next use
\autoref{thm:realup-terminal-common-refinement-splice-uniqueness}. Pairwise
availability of the common-refinement seal pullback fixes the splice between
the accumulated surface and $C_{k+1}$, so all visible classifier, history,
bundle, spine, endpoint, transport, package, and ledger rows agree on the
same finite surface.

Finally apply \autoref{thm:streamname-realup-common-refinement-seal-pullback}
to identify that surface with the terminal consumer boundary. The cited
terminality, route-determinacy, splice-uniqueness, and pullback results expose
only the rows listed in the statement, so the factorization cannot read any
completion, quotient, host, metric, arithmetic, order, or bridge data.
\end{proof}
