\begin{theorem}[AxiomDependencyTuple kernel supply visibility]
\label{thm:axiom-dependency-tuple-kernel-supply-visibility}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, every external assumption read by the kernel side of the
tuple is exposed first as a row of the displayed required-supply ledger $S$.
In particular, host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, ambient classical theorem
names, and any other non-BEDC supply name can be consumed only through the
ledger row selected by $M$ and attached to the witness row $W$.
\end{theorem}
\begin{proof}
Start with \autoref{def:axiom-dependency-tuple-carrier}. The carrier displays
the mode row $M$, witness row $W$, required-supply ledger $S$, transport row
$H$, continuation row $C$, provenance row $P$, and local NameCert row $N$ as
separate finite coordinates.

Apply \autoref{thm:axiom-dependency-tuple-namecert-obligations}. The local
certificate exposes carrier admission, mode classification, witness transport,
ledger exactness, displayed continuation readback, provenance, and naming, so
the kernel-side reader has no hidden coordinate from which to obtain an
external assumption.

The mode split fixes how the ledger is read. By
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}, Mode A has no external
supply, Mode B consumes a restricted witness under the displayed ledger, and
Mode C names refused supply through a counterexample or socket. By
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}, each named host or
classical item therefore remains visible in $S$ before $W$ is consumed.
\end{proof}

\begin{theorem}[AxiomDependencyTuple external supply refusal]
\label{thm:axiom-dependency-tuple-external-supply-refusal}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, the names for host conversion, quotient equality,
$\mathsf{Classical.choice}$, $\mathsf{propext}$, and ambient classical theorem
supply are refused as exported BEDC proof data. They may appear as entries of
$S$ or as refused supply named by $W$ in the appropriate mode, but $H$, $C$,
$P$, and $N$ can only transport, replay, record provenance for, and name the
displayed tuple rows.
\end{theorem}
\leanchecked{BEDC.Derived.AxiomDependencyTupleUp.AxiomDependencyTupleExternalSupplyRefusal}
\begin{proof}
Use the carrier and NameCert obligations first. By
\autoref{def:axiom-dependency-tuple-carrier} and
\autoref{thm:axiom-dependency-tuple-namecert-obligations}, external supply
names occur only in the required-supply ledger and in the witness reading
selected by the mode row.

The three mode cases separate the possible readings. Mode A is governed by
\autoref{thm:axiom-dependency-tuple-zero-supply-row-separation}, so an empty
external ledger cannot be converted into host or classical proof data. Mode B
is governed by
\autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality}, so a
restricted witness is consumed only with the full displayed ledger. Mode C is
governed by
\autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport}, so a
counterexample or socket names missing supply without discharging it.

Finally apply \autoref{thm:axiom-dependency-tuple-supply-ledger-readback},
\autoref{thm:axiom-dependency-tuple-route-nonexport}, and
\autoref{thm:axiom-dependency-tuple-host-supply-nonescape}. Ledger readback
keeps the names visible, route non-export prevents continuation replay from
creating proof rules, and host-supply nonescape keeps every such name inside
the audit ledger surface.
\end{proof}

\begin{theorem}[AxiomDependencyTuple audit consumer completeness]
\label{thm:axiom-dependency-tuple-audit-consumer-completeness}
Every dependency-map consumer for an accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$ must read the complete audit surface: mode $M$, witness
$W$, required-supply ledger $S$, transport row $H$, continuation route $C$,
provenance row $P$, and local NameCert row $N$. A consumer that omits any one
of these rows is not a consumer of the displayed dependency tuple.
\end{theorem}
\begin{proof}
Begin with the finite packet of
\autoref{def:axiom-dependency-tuple-carrier}. Its public surface is exactly
$M,W,S,H,C,P,N$, so the consumer question is a row-coverage question rather
than a request for an ambient proof principle.

The first three rows are forced by the obligation and mode theorems. Apply
\autoref{thm:axiom-dependency-tuple-namecert-obligations},
\autoref{thm:axiom-dependency-tuple-mode-exhaustion}, and
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback}: the consumer must
know which mode is active, which witness is being read, and which ledger row
authorizes or refuses that witness.

The remaining rows are forced by the transport and routing surface. The
existing per-mode separation theorems keep the three witness readings disjoint,
while \autoref{thm:axiom-dependency-tuple-route-nonexport} and
\autoref{thm:axiom-dependency-tuple-consumer-exhaustion} confine every consumer
to the displayed packet rows. Hence a complete audit consumer must pass through
$H$, $C$, $P$, and $N$ as well as $M$, $W$, and $S$.
\end{proof}

\begin{corollary}[AxiomDependencyTuple kernel supply visibility strict obstruction]
\label{cor:axiom-dependency-tuple-kernel-supply-visibility-strict-obstruction}
For every accepted $\AxiomDependencyTupleUp$ carrier
$A=(M,W,S,H,C,P,N)$, any displayed failure, refusal, separation, or
counterexample-or-socket row used in the kernel-supply visibility argument has
strictly local force. It blocks only the named converse or reuse route that
tries to read external supply outside the required-supply ledger $S$, erase a
listed supply entry, reread a mode as another mode, or export refused supply as
BEDC proof data. It cannot be reinterpreted as a global impossibility for
$\AxiomDependencyTupleUp$, as a host theorem, or as hidden external validation.
Every consumer-facing use of the obstruction factors through one of the
displayed rows $M,W,S,H,C,P,N$ and rejects any unlisted coordinate.
\end{corollary}
\begin{proof}
Start with \autoref{thm:axiom-dependency-tuple-kernel-supply-visibility}. Any
external assumption read by the kernel side is visible first as a row of the
required-supply ledger $S$, selected by the mode row $M$ and attached to the
witness row $W$. Thus the obstruction has a named input surface before any
consumer can use it.

Now apply \autoref{thm:axiom-dependency-tuple-external-supply-refusal}. Host
conversion, quotient equality, $\mathsf{Classical.choice}$, $\mathsf{propext}$,
and ambient classical theorem supply may be named in $S$ or by the refused
witness reading, but the rows $H$, $C$, $P$, and $N$ can only transport,
replay, record provenance for, and name the displayed tuple rows. Hence a
consumer-facing obstruction has the listed route, transport, provenance, and
NameCert coordinates as its whole interface.

The three mode rows give the strict local cases. In Mode A,
\autoref{thm:axiom-dependency-tuple-zero-supply-row-separation} says that the
empty external ledger remains separate from the zero-supply witness, so the
blocked route is only the attempted conversion of emptiness into host or
classical proof data. In Mode B,
\autoref{thm:axiom-dependency-tuple-restricted-supply-ledger-totality} says that
the restricted witness is consumed only with the full displayed ledger, so the
blocked route is only subledger erasure, ledger shrinking, or replacement by an
implicit host rule. In Mode C,
\autoref{thm:axiom-dependency-tuple-counterexample-socket-nonexport} says that a
counterexample or socket names refused supply without discharging it, so the
blocked route is only promotion of that refusal into an exported BEDC rule.

It remains to exclude broader readings. By
\autoref{thm:axiom-dependency-tuple-supply-ledger-readback},
\autoref{thm:axiom-dependency-tuple-route-nonexport}, and
\autoref{thm:axiom-dependency-tuple-host-supply-nonescape}, the obstruction is
read back through the visible ledger, replayed only by displayed routes, and
kept inside the audit surface under transport. By
\autoref{thm:axiom-dependency-tuple-audit-consumer-completeness}, any consumer
that omits one of $M,W,S,H,C,P,N$ is not a consumer of the displayed dependency
tuple. Therefore the row blocks only the named local converse or reuse route,
and no unlisted coordinate can turn it into a global impossibility, host
theorem, or hidden external validation.
\end{proof}
