\begin{theorem}[Finite Lebesgue-number bridge packet exactness]
\label{thm:finite-lebesgue-number-bridge-packet-exactness}
The $\FiniteLebesgueNumberUp$ bridge packet displayed to compact and uniform consumers is exactly
$$
D,W,\lambda,M,H,C,P,N .
$$
The route reads $D$ through $\DyadicCoverUp$, $\lambda$ through $\RationalBallUp$, $M$ through $\DyadicMeshUp$, the finite-window sources through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, and the consumer endpoints through $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$. No coordinate outside this tuple contributes to the bridge packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberBridgePacketExactness}
\begin{proof}
Start with the compact-radius bridge. \autoref{thm:finite-lebesgue-number-compact-radius-bridge} identifies the compact and compact-net radius route as the displayed tuple $D,W,\lambda,M,H,C,P,N$ and forces the read through $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.

Next use source-chain admission and ledger transport. \autoref{thm:finite-lebesgue-number-source-chain-admission} admits the route only after the displayed source rows pass through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet, while \autoref{thm:finite-lebesgue-number-ledger-transport} prevents the positive radius ledger from separating from the cover, mesh, stream, regular-rational, and real rows.

Finally apply uniform-modulus radius scope. \autoref{thm:finite-lebesgue-number-uniform-modulus-radius-scope} sends the uniform consumer through the same positive finite-radius row and excludes any added compactness, completeness, quotient, or external modulus coordinate. Therefore the bridge packet is exactly the displayed tuple.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact-uniform bridge soundness]
\label{thm:finite-lebesgue-number-compact-uniform-bridge-soundness}
Every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives the same finite radius route
$$
D,W,\lambda,M,H,C,P,N .
$$
The compact and uniform endpoints may inspect the displayed dyadic cover, rational-ball radius, mesh ledger, stream source, regular-rational approximation, real row, transport rows, continuations, package provenance, and local $\NameCert$ row; they do not receive an open-cover coordinate, a subcover-choice coordinate, or an external radius-modulus coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactUniformBridgeSoundness}
\begin{proof}
First fix the compact side. \autoref{thm:finite-lebesgue-number-compact-radius-bridge} sends $\CompactMetricUp$ and $\CompactNetModulusSelectorUp$ consumers through the displayed positive finite-radius route and excludes open-cover compactness, selected subcovers, host minima, quotient equality, and external radius selectors.

Now fix the uniform side. \autoref{thm:finite-lebesgue-number-uniform-modulus-radius-scope} states that a $\UniformModulusUp$ handoff reads only the displayed radius row in the same tuple and cannot add host compactness, real completeness, quotient equality, or an external modulus function.

The dyadic-cover Real route supplies the shared source order. \autoref{thm:finite-lebesgue-number-dyadic-cover-real-route} forces finite-window reads through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before mesh and cover-cell readback. Thus compact, compact-net, and uniform consumers receive one finite radius route rather than separate compactness or choice surfaces.
\end{proof}

\begin{theorem}[Finite Lebesgue-number bridge nonescape]
\label{thm:finite-lebesgue-number-bridge-nonescape}
The $\FiniteLebesgueNumberUp$ bridge packet cannot import host compactness, selected subcovers, quotient equality, $\RealUp$ completeness, or external modulus data. Every bridge-facing read remains inside the displayed dyadic finite-cover route
$$
D,W,\lambda,M,H,C,P,N .
$$
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberBridgeNonescape}
\begin{proof}
Use the consumer nonescape triad. \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} excludes open-cover compactness, host minima, selected subcovers, quotient equality, choice, and external modulus data for compact, compact-net, and uniform consumers.

Next use compact-uniform bridge soundness. \autoref{thm:finite-lebesgue-number-compact-uniform-bridge-soundness} identifies the only consumer route as $D,W,\lambda,M,H,C,P,N$ and lists the permitted cover, radius, mesh, stream, regular-rational, real, transport, continuation, provenance, and naming rows.

Finally use bridge packet exactness. \autoref{thm:finite-lebesgue-number-bridge-packet-exactness} leaves no bridge coordinate outside the displayed tuple. Hence none of host compactness, selected subcovers, quotient equality, real completeness, or external modulus data can enter the bridge packet.
\end{proof}

\closureat{FiniteLebesgueNumberUp}{seedStr}
\closureat{FiniteLebesgueNumberUp}{obligationStr}
\closureat{FiniteLebesgueNumberUp}{scopedStr}
\closureat{FiniteLebesgueNumberUp}{publicStr}

\begin{closurestatus}{\FiniteLebesgueNumberUp}
  \constructivestory{A $\FiniteLebesgueNumberUp$ packet is generated from an accepted $\DyadicCoverUp$ finite cover, a $\FiniteWindowEnvelopeUp$ row, a positive rational radius ledger, a $\DyadicMeshUp$ refinement ledger, displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public finite-cover radius route is closed by the carrier, local NameCert obligations, root unblock package, selector-radius domain, compact-net selector factorization, uniform-modulus radius exhaustion, radius lower-bound fold \autoref{def:finite-lebesgue-number-radius-lower-bound-fold}, cover-shrinkage stability \autoref{thm:finite-lebesgue-number-cover-shrinkage-stability}, UniformModulus consumer exactness \autoref{thm:finite-lebesgue-number-uniform-modulus-consumer-exactness}, radius-modulus transport scope \autoref{thm:finite-lebesgue-number-radius-modulus-transport-scope}, compact uniform handoff scope \autoref{thm:finite-lebesgue-number-compact-uniform-handoff-scope}, scoped closure package \autoref{thm:finite-lebesgue-number-scoped-closure-package}, radius-cover monotone readback \autoref{thm:finite-lebesgue-number-radius-cover-monotone-readback}, mesh-refinement cover exhaustion \autoref{thm:finite-lebesgue-number-mesh-refinement-cover-exhaustion}, compact-route dyadic modulus package \autoref{thm:finite-lebesgue-number-compact-route-dyadic-modulus-package}, public compact-uniform export \autoref{thm:finite-lebesgue-number-public-compact-uniform-export}, bridge packet exactness \autoref{thm:finite-lebesgue-number-bridge-packet-exactness}, compact-uniform bridge soundness \autoref{thm:finite-lebesgue-number-compact-uniform-bridge-soundness}, and bridge nonescape \autoref{thm:finite-lebesgue-number-bridge-nonescape}.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close open-cover compactness, arbitrary subcover choice, host real compactness, total-bounded construction, Lean verification, or bridge checking.}
  \upgradepath{The remaining obligation is Lean verification and bridge checking for the displayed finite dyadic-cover packet.}
\end{closurestatus}
