\begin{theorem}[Finite Lebesgue-number L10 sibling route]
\label{thm:finite-lebesgue-number-l10-sibling-route}
Every accepted $\FiniteLebesgueNumberUp$ consumer route that exposes the positive finite-radius ledger to a compact, compact-net, continuous-map, or uniform-modulus consumer factors through the L10 finite-name chain
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert},
\autoref{ch:concrete-instances-dyadicratcore-namecert}, and
\autoref{ch:concrete-instances-real-namecert},
and then through the dyadic mesh and cover surfaces of
\autoref{ch:concrete-instances-dyadicmesh-namecert} and
\autoref{ch:concrete-instances-dyadiccover-namecert}. Thus a compact-continuous consumer can read the positive radius only as part of the displayed finite route
$$
D,W,\lambda,M,H,C,P,N .
$$
The route has no coordinate for open-cover compactness, host minima, selected subcovers, quotient equality, choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the root carrier and NameCert obligations. \autoref{def:finite-lebesgue-number-carrier} displays $D,W,\lambda,M,H,C,P,N$, while \autoref{thm:finite-lebesgue-number-namecert-obligations} makes every radius, mesh, window, transport, continuation, provenance, and local naming read a finite component of that packet.

Next attach the source-accountability rows. \autoref{thm:finite-lebesgue-number-compact-radius-source-accountability} forces compact and compact-net radius reads through the visible $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicMeshUp$, and $\DyadicCoverUp$ surface. \autoref{thm:finite-lebesgue-number-selected-tail-radius-admission} inserts the selected-tail $\DyadicRatCoreUp$ seal before the compact-net selector consumes the radius.

The selected-tail bridge ledger then keeps the source route finite. Its packet $J$ records the stream-window, regular-rational readback, dyadic tolerance ledger, real seal, finite Lebesgue radius row, and the same $H,C,P,N$ support; no row in $J$ supplies an open family, a host minimum, a quotient equality principle, or an ambient completeness theorem.

Finally apply the compact-continuous triad. \autoref{thm:finite-lebesgue-number-compact-continuous-triad} and \autoref{thm:finite-lebesgue-number-uniform-continuity-handoff} make $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ consumers read the same finite dyadic-radius packet. Hence every accepted compact-continuous route factors through the displayed L10 sibling chain before the positive radius is visible, and the excluded compactness, selection, equality, choice, and completeness data remain absent.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberL10SiblingRoute}
