\begin{theorem}[Finite Lebesgue-number L10 phase consumer readiness]
\label{thm:finite-lebesgue-number-l10-phase-consumer-readiness}
Every accepted $\FiniteLebesgueNumberUp$ consumer route used at the Phase Real or Completion boundary factors through the finite packet over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Continuous-map and totally-bounded consumers read the same route through the displayed compact-uniform handoff. The route exports no open-cover compactness, selected subcover, host minimum, quotient equality, choice, external modulus, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the compact-uniform export. \autoref{thm:finite-lebesgue-number-public-compact-uniform-export} identifies the public handoff as the finite dyadic-cover, rational-ball, mesh, stream, regular-rational, Real, transport, replay, provenance, naming, and compact-net selector packet.

Next attach the L10 source chain. \autoref{thm:finite-lebesgue-number-dyadic-cover-real-route} sends each finite-window read through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before mesh and cover-cell readback, and \autoref{thm:finite-lebesgue-number-source-chain-admission} places the displayed dyadic rows in the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.

Use ledger transport to keep the route stable. \autoref{thm:finite-lebesgue-number-ledger-transport} preserves the positive radius ledger together with the cover, mesh, stream, regular-rational, and Real rows under $\hsame$ transport, so later compact, continuous-map, totally-bounded, uniform-modulus, or Completion-facing consumers cannot detach a scalar or host-side witness from the packet.

Finally apply the nonescape boundary. \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} excludes open-cover compactness, host minima, selected subcovers, quotient equality, choice, and external modulus data from the compact, compact-net, and uniform consumer endpoints. Since the Phase Real and Completion handoffs read through those endpoints and the same L10 source packet, their consumer-ready route is exactly the displayed finite packet and not an additional compactness, choice, modulus, or completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberL10PhaseConsumerReadiness}

\begin{theorem}[Finite Lebesgue-number L10 consumer readback exactness]
\label{thm:finite-lebesgue-number-l10-consumer-readback-exactness}
Every Phase Real or Completion boundary consumer of an accepted $\FiniteLebesgueNumberUp$ route reads exactly the packet over
$$
\DyadicCoverUp,\RationalBallUp,\DyadicMeshUp,\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
The compact, compact-net, continuous-map, totally-bounded, and uniform-modulus endpoints add no open-cover compactness, selected subcover, host minimum, quotient equality, choice, external modulus, selected limit, or detached Real-completeness row to that consumer-visible readback.
\end{theorem}
\begin{proof}
First identify the endpoint factorization. \autoref{thm:finite-lebesgue-number-l10-phase-consumer-readiness} places every Phase Real or Completion boundary consumer on the finite route through the dyadic cover, rational-ball, dyadic mesh, stream, regular-rational, Real, compact, compact-net, uniform, and structural rows, with no outside compactness, equality, choice, modulus, or completeness coordinate.

Next read the source packet through the open Phase classifier. \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} identifies the accepted positive-radius read with the four-face route
$$
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp
$$
together with the $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Finally assemble the terminal package. \autoref{thm:finite-lebesgue-number-root-unblock-terminal-package} states that the open Phase pullback, compact-uniform readiness, Real-completion terminal-radius exhaustion, and L10 phase consumer readiness are one certificate over exactly the displayed packet. Since that terminal certificate has no coordinate for open-cover compactness, selected subcovers, host minima, quotient equality, choice, external moduli, selected limits, or detached Real completeness, the consumer-visible readback is exactly the finite packet named in the statement.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberL10ConsumerReadbackExactness}
