\chapter{A Concrete Naming Certificate for $\FiniteLebesgueNumberUp$}
\label{ch:concrete-instances-finite-lebesgue-number-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the finite Lebesgue-number route used here is a displayed dyadic finite-cover modulus. The $\FiniteLebesgueNumberUp$ packet records a finite dyadic cover, a positive rational radius ledger, and the finite-window witnesses needed by total-bounded and compact-metric consumers. It is not an open-cover compactness principle and it does not choose a subcover from an arbitrary family.

The finite radius ledger is consumed by the compact-metric route of \autoref{ch:concrete-instances-compactmetric-namecert} and is built over the explicit dyadic-cover surface of \autoref{ch:concrete-instances-dyadiccover-namecert}.

\begin{definition}[Finite Lebesgue-number carrier]
\label{def:finite-lebesgue-number-carrier}
A $\FiniteLebesgueNumberUp$ carrier over a displayed $\DyadicCoverUp$ row is a finite $\BHist$ packet
$$
L=(D,W,\lambda,M,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $D$ is the accepted $\DyadicCoverUp$ row containing the finite list of dyadic centers, rational ball rows, dyadic mesh cells, and finite coverage witnesses;
\item $W$ is the $\FiniteWindowEnvelopeUp$ row whose inspected points are covered by the dyadic cells of $D$;
\item $\lambda$ is the positive finite radius ledger, read through $\RationalBallUp$ and bounded by the radii recorded in $D$;
\item $M$ is the $\DyadicMeshUp$ mesh ledger that records which mesh cells refine into the $\lambda$-balls and into the cover cells of $D$;
\item $H$ records componentwise $\hsame$ transports for $D$, $W$, $\lambda$, $M$, the $\StreamNameUp$ reads, the $\RegSeqRatUp$ approximation rows, and the $\RealUp$ consumer rows;
\item $C$ records the displayed $\Cont$ routes by which consumers inspect finite-window membership, rational-ball containment, dyadic-mesh refinement, stream-name reads, regular-rational approximations, and real rows;
\item $P$ is the $\Pkg$ provenance over $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\DyadicMeshUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and the local certificate rows;
\item $N$ is the local $\NameCert_{\FiniteLebesgueNumberUp}$ row.
\end{enumerate}
The carrier accepts only packets whose positive finite radius ledger is displayed beside the finite dyadic cover and whose mesh witnesses keep every admitted finite-window read inside a named cover cell.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier}

\begin{theorem}[Finite Lebesgue-number NameCert obligations]
\label{thm:finite-lebesgue-number-namecert-obligations}
The local $\NameCert_{\FiniteLebesgueNumberUp}$ surface consists of five finite rows:
\begin{enumerate}
\item carrier: the packet of \autoref{def:finite-lebesgue-number-carrier};
\item classifier: componentwise comparison of the dyadic cover row, finite-window row, positive radius ledger, mesh ledger, transports, continuations, package provenance, and local certificate row;
\item radius-modulus stability: displayed $\hsame$ and $\Cont$ transport preserves the positive ledger $\lambda$ together with the $\RationalBallUp$ and $\DyadicMeshUp$ rows that witness its refinement into the finite cover;
\item finite-window coverage exactness: every accepted point read from $W$ factors through a $\StreamNameUp$ row, a $\RegSeqRatUp$ approximation row, a $\RealUp$ row, a mesh cell from $M$, and a named cover cell in $D$;
\item non-escape: accepted packets export no open-cover compactness theorem, no arbitrary subcover selector, no host compactness principle, and no hidden cover family outside the displayed dyadic finite-cover data.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier\_namecert\_obligations}
\begin{proof}
Carrier habitation is the displayed tuple $L=(D,W,\lambda,M,H,C,P,N)$. The dyadic cover, finite-window row, radius ledger, mesh ledger, transports, continuations, package provenance, and local certificate are all finite coordinates.

The classifier is componentwise on those coordinates. Radius-modulus stability follows by transporting the positive rational radius ledger and the mesh-refinement rows along $H$, then replaying only the routes stored in $C$.

Coverage exactness is a finite witness read. Each admitted point of $W$ is observed through its stream and regular-rational approximation rows, placed in a real row, assigned to a mesh cell of $M$, and then routed to a named cover cell in $D$.

The carrier has no coordinate for an arbitrary open family, an open-cover compactness theorem, or a subcover selector. Thus every accepted export remains inside the displayed dyadic finite-cover packet.
\end{proof}

\begin{theorem}[Finite Lebesgue-number dyadic cover handoff]
\label{thm:finite-lebesgue-number-dyadic-cover-handoff}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives only the displayed $\DyadicCoverUp$ finite cover, the $\FiniteWindowEnvelopeUp$ coverage row, the positive finite radius ledger $\lambda$, the $\DyadicMeshUp$ refinement ledger $M$, and the listed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance rows. The handoff supplies a finite dyadic-cover modulus and a positive finite radius ledger, not open-cover compactness or subcover choice.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberDyadicCoverHandoff}
\begin{proof}
Project the carrier of \autoref{def:finite-lebesgue-number-carrier}. The only consumer-facing cover data are $D$, $W$, $\lambda$, $M$, $H$, $C$, $P$, and $N$.

Use \autoref{thm:finite-lebesgue-number-namecert-obligations}. Its classifier, radius-modulus stability, and finite-window coverage exactness rows keep every consumer read on the displayed dyadic cover, finite-window witnesses, rational-ball radius ledger, and mesh-refinement ledger.

A total-bounded or compact-metric consumer therefore receives the finite dyadic cover together with the positive radius ledger and provenance rows. Since the carrier contains no arbitrary open family and no selected subcover coordinate, the handoff cannot assert open-cover compactness.
\end{proof}

\begin{theorem}[Finite Lebesgue-number radius transport]
\label{thm:finite-lebesgue-number-radius-transport}
Let $L=(D,W,\lambda,M,H,C,P,N)$ be an accepted $\FiniteLebesgueNumberUp$ carrier. For every componentwise $\hsame$ transport recorded in $H$, the transported packet preserves the positive finite radius ledger $\lambda$, the $\RationalBallUp$ radius readback attached to $\lambda$, and the $\DyadicMeshUp$ refinement rows in $M$ as one finite packet. In particular, a consumer cannot transport the radius coordinate without simultaneously transporting the rational-ball and mesh-refinement evidence by which the radius is read.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRadiusTransport}
\begin{proof}
Project the accepted carrier of \autoref{def:finite-lebesgue-number-carrier}. The radius coordinate is not stored as an isolated scalar: it is bundled with the rational-ball readback, the mesh ledger, the componentwise transport rows, and the displayed continuation routes.

Use the radius-modulus stability row of \autoref{thm:finite-lebesgue-number-namecert-obligations}. That row transports $\lambda$ only together with the $\RationalBallUp$ and $\DyadicMeshUp$ rows witnessing refinement into the finite cover.

Therefore every transported radius read remains in the finite packet $D,W,\lambda,M,H,C,P,N$. No additional radius selector, host metric radius, or open-cover radius coordinate is exposed.
\end{proof}

\begin{theorem}[Finite Lebesgue-number finite-window coverage exactness]
\label{thm:finite-lebesgue-number-window-coverage-exactness}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, every accepted finite-window read factors through the displayed window $W$, then through a $\StreamNameUp$ row, a $\RegSeqRatUp$ approximation row, a $\RealUp$ row, a mesh cell of $M$, and a named cover cell of $D$. The factorization has no coordinate for an arbitrary open family, no host compactness witness, and no selected subcover outside the displayed dyadic finite-cover packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberWindowCoverageExactness}
\begin{proof}
Start with an accepted read from $W$. By the finite-window coverage exactness row of \autoref{thm:finite-lebesgue-number-namecert-obligations}, the read is observed through a named stream row, its regular-rational approximation row, and the corresponding real row.

The same exactness row then routes the real read into a displayed mesh cell of $M$ and from that mesh cell into a named cover cell of $D$. These are coordinates of the carrier, so the factorization is finite and internal to $L$.

The non-escape row of \autoref{thm:finite-lebesgue-number-namecert-obligations} excludes open-family, compactness, and selected-subcover coordinates. Hence every accepted finite-window read is exhausted by the displayed route.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact consumer route]
\label{thm:finite-lebesgue-number-compact-consumer-route}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives the carrier route in the order $D,W,\lambda,M,H,C,P,N$: the dyadic cover row, finite-window row, positive radius ledger, mesh refinement ledger, transport rows, continuation routes, package provenance, and local naming row. The consumer cannot read open-cover compactness, host compactness, or a selected subcover from the packet.
\end{theorem}
\begin{proof}
Use \autoref{thm:finite-lebesgue-number-dyadic-cover-handoff}. It identifies the public consumer-facing data as $D,W,\lambda,M,H,C,P,N$ and states that the handoff supplies a finite dyadic-cover modulus and positive finite radius ledger.

Next use \autoref{thm:finite-lebesgue-number-radius-transport}. It keeps the positive radius read tied to the rational-ball and mesh-refinement evidence, so a compact consumer cannot detach the radius from the displayed packet.

Finally use \autoref{thm:finite-lebesgue-number-window-coverage-exactness}. Every finite-window read is routed through $W$, stream and regular-rational rows, a real row, a mesh cell of $M$, and a named cover cell of $D$.

The non-escape clauses in these three rows leave no coordinate for open-cover compactness, host compactness, or selected subcover data. Thus the compact consumer route is exactly the ordered carrier route.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier\_compact\_consumer\_route}

\begin{theorem}[Finite radius nonchoice obligation]
\label{thm:finite-lebesgue-number-finite-radius-nonchoice}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the positive radius ledger $\lambda$ is readable only through the displayed $\RationalBallUp$ radius rows of $D$ and the $\DyadicMeshUp$ refinement rows of $M$. No consumer route in the packet reads $\lambda$ by invoking an open-cover choice principle, an arbitrary subcover selector, or a host compactness witness outside $D,W,\lambda,M,H,C,P,N$.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:finite-lebesgue-number-carrier}. Its radius coordinate is listed between the finite-window row $W$ and the mesh ledger $M$, and its admissible readback is explicitly through the rational-ball and dyadic-mesh rows.

Apply the radius-modulus stability row of \autoref{thm:finite-lebesgue-number-namecert-obligations} and the transport statement of \autoref{thm:finite-lebesgue-number-radius-transport}. They keep $\lambda$ attached to the $\RationalBallUp$ rows and to the $\DyadicMeshUp$ refinement evidence under every stored $\hsame$ transport and every replayed $\Cont$ route.

The compact consumer route of \autoref{thm:finite-lebesgue-number-compact-consumer-route} exposes the ordered packet $D,W,\lambda,M,H,C,P,N$ and no other cover coordinate. Since the packet contains no open-cover family and no subcover selector, the radius obligation is finite and nonchoice.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberFiniteRadiusNonchoice}

\begin{theorem}[Mesh refinement nonchoice obligation]
\label{thm:finite-lebesgue-number-mesh-refinement-nonchoice}
Let $L=(D,W,\lambda,M,H,C,P,N)$ be an accepted $\FiniteLebesgueNumberUp$ carrier. Refinement from a mesh cell recorded in $M$ to a cover cell recorded in $D$ is stable under the stored $\hsame$ transports in $H$ and under the replayed $\Cont$ routes in $C$. Thus the mesh-to-cover handoff is determined by the displayed $\DyadicMeshUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows, not by a separately chosen open subcover.
\end{theorem}
\begin{proof}
Use the finite-window coverage exactness theorem \autoref{thm:finite-lebesgue-number-window-coverage-exactness}. An accepted read is first routed through $W$, then through a $\StreamNameUp$ row, a $\RegSeqRatUp$ approximation row, a $\RealUp$ row, a mesh cell of $M$, and finally a named cover cell of $D$.

The NameCert obligations of \autoref{thm:finite-lebesgue-number-namecert-obligations} make this route componentwise. The same rows transport the mesh ledger and the cover-cell witness along $H$, while the continuations in $C$ replay the finite-window membership, rational-ball containment, and mesh-refinement reads.

It follows that changing representatives by $\hsame$ does not detach the mesh cell from its named cover cell. The handoff remains inside $D,W,\lambda,M,H,C,P,N$, so no open-cover compactness theorem or arbitrary subcover coordinate can supply a different refinement route.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier\_mesh\_refinement\_nonchoice}

\begin{theorem}[Total-bounded handoff obligation]
\label{thm:finite-lebesgue-number-total-bounded-handoff}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives exactly the ordered packet
$$
D,W,\lambda,M,H,C,P,N .
$$
The consumer may inspect the displayed $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows in that packet, but cannot recover open-cover compactness, host compactness, arbitrary subcover selection, or a hidden cover family from it.
\end{theorem}
\begin{proof}
The carrier definition fixes the visible order $D,W,\lambda,M,H,C,P,N$. The compact consumer route of \autoref{thm:finite-lebesgue-number-compact-consumer-route} states that this is the consumer-facing order for both $\TotallyBoundedUp$ and $\CompactMetricUp$ reads.

The finite radius obligation of \autoref{thm:finite-lebesgue-number-finite-radius-nonchoice} keeps the radius ledger tied to the displayed rational-ball and mesh rows. The mesh refinement obligation of \autoref{thm:finite-lebesgue-number-mesh-refinement-nonchoice} keeps the mesh-to-cover read stable under stored transports and replayed continuations.

Together with the dyadic cover handoff of \autoref{thm:finite-lebesgue-number-dyadic-cover-handoff}, these rows exhaust the public data a total-bounded or compact-metric consumer receives. The non-escape row of \autoref{thm:finite-lebesgue-number-namecert-obligations} excludes open-cover compactness and arbitrary subcover selection, so the handoff is exactly the finite BEDC packet.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier\_total\_bounded\_handoff}

\begin{theorem}[Compact-uniform selector handoff]
\label{thm:finite-lebesgue-number-compact-uniform-selector-handoff}
Every accepted $\FiniteLebesgueNumberUp$ carrier consumed by a compact-uniform route supplies exactly the positive radius ledger read by $\CompactNetModulusSelectorUp$, and then by $\UniformModulusUp$, through the displayed $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It supplies no open-cover compactness, host minimum, selected subcover, quotient equality, or external modulus function.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactUniformSelectorHandoff}
\begin{proof}
Project the finite Lebesgue-number carrier $L=(D,W,\lambda,M,H,C,P,N)$. The positive ledger $\lambda$ is displayed between the finite-window row and the mesh row, so any compact-uniform consumer reads it as part of the same finite packet.

Invoke the dyadic cover handoff, radius transport, and finite-window coverage exactness theorems. These route the radius through $D$, $W$, the $\RationalBallUp$ readback, the $\DyadicMeshUp$ refinements, and the stored $\hsame$ and $\Cont$ rows.

Apply the total-bounded handoff theorem above. It identifies $D,W,\lambda,M,H,C,P,N$ as the exact packet delivered to total-bounded and compact-metric consumers, so the compact-uniform route receives no hidden compactness witness in addition to the finite radius ledger.

The compact-net selector and uniform-modulus chapters are the downstream consumers of this displayed packet. The selector reads the positive radius ledger as its compact-net input, and the uniform-modulus surface reads the resulting tolerance-only route. Since open-cover compactness, host minima, selected subcovers, quotient equality, and external modulus functions are absent from $L$, the handoff is exactly the finite BEDC radius-ledger route.
\end{proof}

\begin{theorem}[Window-radius ledger coherence]
\label{thm:finite-lebesgue-number-window-radius-ledger-coherence}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, every finite-window read in $W$ is coherent with the positive radius ledger $\lambda$ only through the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. A compact consumer cannot read a finite window first and then attach an unrelated positive radius outside $D,W,\lambda,M,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberWindowRadiusLedgerCoherence}
\begin{proof}
Project the displayed carrier. The finite-window row $W$ and positive radius ledger $\lambda$ are coordinates of the same packet, and the local NameCert obligations name them together.

Use radius transport and finite-window coverage exactness. The radius row is preserved by the stored $\hsame$ transport and replayed $\Cont$ route, while the finite-window row is read through the dyadic cover and mesh rows already present in $D$ and $M$.

Apply the compact-uniform selector handoff above. The downstream compact route receives the ordered finite packet, so any radius attached after the window read must be the displayed ledger $\lambda$ rather than an external compactness choice.
\end{proof}

\begin{theorem}[Cover-cell readback totality]
\label{thm:finite-lebesgue-number-cover-cell-readback-totality}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, each read from the finite-window row $W$ reaches a named dyadic cover cell through $D,W,\lambda,M,H,C,P,N$. The readback first consumes the window row, then the positive radius ledger and mesh row, then the componentwise transport, replay, provenance, and local naming rows; no open-cover family or arbitrary cell selector supplies the endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCoverCellReadbackTotality}
\begin{proof}
Start from finite-window coverage exactness. It sends every accepted window read through the displayed stream, regular-rational, real, mesh, and cover rows.

The mesh refinement and radius transport obligations keep that endpoint tied to $M$ and $\lambda$ under the same $H$ and $C$ routes. Thus the cover cell is not selected by a separate open-cover principle.

Finally, $P$ and $N$ package and name the readback as part of the same $\FiniteLebesgueNumberUp$ carrier. This gives total cover-cell readback for the finite dyadic route.
\end{proof}

\begin{theorem}[L10 source-lock for compact radius reads]
\label{thm:finite-lebesgue-number-l10-source-lock}
Every accepted $\FiniteLebesgueNumberUp$ public finite-window read locks its radius route through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicMeshUp$, and $\DyadicCoverUp$ before any $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, or $\UniformModulusUp$ consumer may read the positive radius ledger. The consumer-facing read is therefore a read of the displayed packet $D,W,\lambda,M,H,C,P,N$, not a radius read supplied by an external compactness or modulus interface.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberL10SourceLock}
\begin{proof}
Begin with finite-window coverage exactness. It forces each accepted finite-window read to pass through the displayed stream, regular-rational, real, mesh, and cover rows before it can be used as a cover read.

The radius transport and mesh-refinement nonchoice theorems keep the positive ledger $\lambda$ tied to that same window and mesh route. Hence a compact consumer cannot detach the radius from $W$ and $M$ and then attach a different compactness witness.

Finally apply the compact-uniform selector handoff and cover-cell readback totality. They identify the downstream compact and uniform readers as consumers of the named finite packet $D,W,\lambda,M,H,C,P,N$, so the L10 source route is locked before any positive radius ledger is exposed.
\end{proof}

\begin{theorem}[Stream-regular window order]
\label{thm:finite-lebesgue-number-stream-regular-window-order}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, each public finite-window read is ordered as follows: first the window row $W$, then the $\StreamNameUp$ row, then the $\RegSeqRatUp$ approximation row, then the $\RealUp$ row, then a mesh cell in $M$, then a cover cell in $D$, and finally the support rows $H,C,P,N$. Componentwise $\hsame$ transport and the displayed $\Cont$ replay preserve that order.
\end{theorem}
\begin{proof}
Use finite-window coverage exactness to read the window row through the displayed stream, regular-rational, real, mesh, and cover rows. This fixes the forward route from $W$ to the named cell of $D$ through $M$.

Use radius transport and mesh-refinement nonchoice to preserve the same order under componentwise $\hsame$ transport. The positive ledger $\lambda$ remains between the finite window and mesh rows, so the mesh cell in $M$ cannot be read before the regular and real source rows have been displayed.

The compact-uniform selector handoff and cover-cell readback totality then package the route with $H,C,P,N$. The $\Cont$ replay is therefore an order-preserving replay of the already displayed finite packet, not a new path that bypasses the stream or regular-Cauchy source.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberStreamRegularWindowOrder}

\begin{theorem}[Real source nonchoice boundary]
\label{thm:finite-lebesgue-number-real-source-nonchoice}
For every accepted $\FiniteLebesgueNumberUp$ carrier, the $\RealUp$ row used by a compact or uniform consumer is read only through the displayed $\StreamNameUp$ and $\RegSeqRatUp$ source rows. It is not read by host real equality, an arbitrary point selector, open-cover compactness, a subcover choice principle, or any external real representative outside $D,W,\lambda,M,H,C,P,N$.
\end{theorem}
\begin{proof}
Start from finite-window coverage exactness. The $\RealUp$ row appears as part of the displayed source chain following the stream-name and regular-rational rows, so the real read is already anchored before the mesh and cover cells are consumed.

Radius transport and mesh-refinement nonchoice keep that real source attached to the positive radius and mesh rows under the same $\hsame$ and $\Cont$ data. Thus host real equality and arbitrary point selection cannot replace the displayed source rows.

The compact-uniform selector handoff and cover-cell readback totality give the downstream boundary. Compact and uniform consumers receive the named finite route, while open-cover compactness, subcover choice, and external representatives are absent from the carrier.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRealSourceNonchoice}

\begin{theorem}[Compact consumer nonchoice boundary]
\label{thm:finite-lebesgue-number-compact-consumer-nonchoice-boundary}
Every $\CompactMetricUp$ or $\CompactNetModulusSelectorUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives only the finite dyadic route through $D,W,\lambda,M,H,C,P,N$. The consumer may use the named cover cells, finite-window reads, positive radius ledger, mesh refinements, transports, continuations, provenance, and local naming, but it receives no open-cover compactness theorem, host compactness witness, arbitrary subcover choice, or external selector.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactConsumerNonchoiceBoundary}
\begin{proof}
Use the compact-uniform selector handoff and the total-bounded handoff. Together they identify the consumer-facing data as the displayed finite carrier $D,W,\lambda,M,H,C,P,N$.

The window-radius coherence theorem keeps window reads and radius reads in the same packet. The cover-cell readback totality theorem then gives named dyadic cover cells without invoking a free subcover selector.

The non-escape row of the local NameCert obligations excludes open-cover compactness, host compactness, and arbitrary selectors. Therefore compact consumers receive only the finite dyadic route.
\end{proof}

\begin{theorem}[Finite Lebesgue-number positive-radius compact-net export]
\label{thm:finite-lebesgue-number-positive-radius-compact-net-export}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the positive-radius ledger exported to $\CompactNetModulusSelectorUp$ is exactly the finite route through $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, and $\CompactNetModulusSelectorUp$ displayed by $D,W,\lambda,M,H,C,P,N$. The export has no open-cover compactness theorem, host minimum, arbitrary subcover selector, quotient equality, or choice coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPositiveRadiusCompactNetExport}
\begin{proof}
Project the carrier. The dyadic cover row $D$, finite-window row $W$, positive radius ledger $\lambda$, mesh row $M$, and support rows $H,C,P,N$ are the only rows available before a compact-net consumer can read the packet.

Use the compact consumer nonchoice boundary. It keeps $\CompactMetricUp$ and $\CompactNetModulusSelectorUp$ consumers inside the finite dyadic route and excludes open-cover compactness, host compactness, arbitrary subcover choice, and external selectors.

The positive finite-radius totality theorem places $\lambda$ before the compact read, while the total-bounded handoff routes the finite cover data through $\TotallyBoundedUp$ and $\CompactMetricUp$. Hence the compact-net export is the displayed finite radius ledger and nothing stronger.
\end{proof}

\begin{theorem}[Finite Lebesgue-number dyadic-cover uniform-modulus handoff]
\label{thm:finite-lebesgue-number-dyadic-cover-uniform-modulus-handoff}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, every $\UniformModulusUp$ consumer receives the dyadic-cover radius route only after the same displayed packet has passed through $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, and $\CompactNetModulusSelectorUp$. The handoff is a finite radius-to-modulus route, not an open-cover compactness argument, selected subcover, host minimum, or external modulus selector.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberDyadicCoverUniformModulusHandoff}
\begin{proof}
Start from the compact-uniform selector handoff. It identifies the downstream compact-net selector and uniform-modulus chapters as consumers of the finite packet $D,W,\lambda,M,H,C,P,N$.

Next apply positive-radius compact-net export. The selector receives the positive-radius ledger only through the displayed dyadic cover, rational-ball, mesh, window, regular-readback, Real, total-bounded, and compact-metric rows.

Finally use the finite radius nonchoice and mesh-refinement nonchoice obligations. These keep the radius and mesh attached to the dyadic packet under $H,C,P,N$, so a $\UniformModulusUp$ consumer cannot substitute an open-cover compactness theorem, host minimum, selected subcover, or external modulus row for the finite handoff.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact-consumer radius-ledger totality]
\label{thm:finite-lebesgue-number-compact-consumer-radius-ledger-totality}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, compact and uniform consumers that preserve the displayed classifier receive a total positive-radius ledger inside the same finite route $D,W,\lambda,M,H,C,P,N$. The ledger is total for the displayed $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumer chain, and it excludes open-cover compactness, host compactness, selected subcovers, hidden minima, quotient equality, and choice.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactConsumerRadiusLedgerTotality}
\begin{proof}
Begin with window-radius ledger coherence. It ties every finite-window read to the same positive-radius ledger $\lambda$ through the displayed carrier rows, so the compact consumer cannot attach an unrelated radius after reading $W$.

Use cover-cell readback totality and dyadic-cover uniform-modulus handoff. The first theorem gives named dyadic cover cells through $D,W,\lambda,M,H,C,P,N$, and the second carries the same positive-radius route to $\CompactNetModulusSelectorUp$ and $\UniformModulusUp$ consumers.

The compact consumer nonchoice boundary supplies the exclusion clause. Since open-cover compactness, host compactness, selected subcovers, hidden minima, quotient equality, and choice coordinates are absent from the packet, the compact-consumer radius ledger is total exactly on the displayed finite route.
\end{proof}

\begin{theorem}[Positive finite-radius totality]
\label{thm:finite-lebesgue-number-positive-radius-totality}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the packet exposes a positive finite radius ledger $\lambda$ before any $\CompactMetricUp$ consumer may read a Lebesgue-number route. The radius is consumed only together with the displayed $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, transport, continuation, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Project the carrier $L=(D,W,\lambda,M,H,C,P,N)$. The radius coordinate is not a host scalar outside the packet; it is placed between the finite-window row and the mesh row.

Use \autoref{thm:finite-lebesgue-number-finite-radius-nonchoice} and \autoref{thm:finite-lebesgue-number-radius-mesh-stability-row}. They keep $\lambda$ attached to rational-ball readback and dyadic-mesh refinement under stored transports and replayed continuations.

Finally apply \autoref{thm:finite-lebesgue-number-total-bounded-handoff}. A compact consumer receives the ordered finite packet only after the positive radius ledger has been displayed, so the Lebesgue-number route has finite-radius totality before it reaches $\CompactMetricUp$.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPositiveRadiusTotality}

\begin{theorem}[Dyadic cover cell selection]
\label{thm:finite-lebesgue-number-dyadic-cover-cell-selection}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, each finite-window read in $W$ lands in a displayed dyadic cover cell of $D$ through the mesh row $M$. The packet supplies no arbitrary subcover selector and no open-cover compactness coordinate outside the displayed dyadic cover, finite-window, radius, mesh, transport, continuation, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Use \autoref{thm:finite-lebesgue-number-window-coverage-exactness}. It routes a finite-window read through stream naming, regular-rational readback, a Real row, a mesh cell of $M$, and then a named cover cell of $D$.

The mesh refinement nonchoice theorem, \autoref{thm:finite-lebesgue-number-mesh-refinement-nonchoice}, keeps that mesh-to-cover handoff stable under the stored $\hsame$ transports and displayed $\Cont$ routes.

Since the carrier contains no open-cover family and no subcover selector, cell selection is exactly the finite dyadic route already displayed by $D,W,\lambda,M,H,C,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberDyadicCoverCellSelection}

\begin{theorem}[Compact-metric handoff exactness]
\label{thm:finite-lebesgue-number-compact-metric-handoff-exactness}
Every $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives only the dyadic cover row $D$, finite-window row $W$, positive-radius ledger $\lambda$, mesh row $M$, componentwise transport row $H$, continuation row $C$, provenance row $P$, and local $\NameCert_{\FiniteLebesgueNumberUp}$ row $N$. It receives no open-cover compactness, host compactness, arbitrary subcover selector, or hidden cover family.
\end{theorem}
\begin{proof}
Start from the total-bounded handoff theorem \autoref{thm:finite-lebesgue-number-total-bounded-handoff}. It identifies $D,W,\lambda,M,H,C,P,N$ as the exact packet delivered to total-bounded and compact-metric consumers.

The positive-radius totality theorem above exposes the finite radius ledger before the compact route is read. The dyadic cover cell-selection theorem above identifies every finite-window read with a displayed dyadic cover cell through $M$.

The non-escape row of \autoref{thm:finite-lebesgue-number-namecert-obligations} excludes open-cover compactness, host compactness, and arbitrary subcover selection. Hence $\CompactMetricUp$ receives exactly the finite-radius dyadic packet and nothing outside it.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.CompactMetricHandoffExactness.FiniteLebesgueNumberCompactMetricHandoffExactness}

\begin{theorem}[Finite-window coverage obligation row]
\label{thm:finite-lebesgue-number-obligation-coverage-row}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the finite-window coverage row factors through $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\DyadicMeshUp$ in that order. A point read from $W$ is accepted only when its stream-name row, regular-rational row, real row, mesh cell, and named dyadic cover cell are all displayed in the same packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberObligationCoverageRow}
\begin{proof}
Start with the finite-window coordinate $W$ in the carrier. The carrier definition already places $W$ beside the dyadic cover $D$ and the mesh ledger $M$, while the finite-window coverage exactness theorem routes each accepted read through stream, regular-rational, real, mesh, and cover rows.

The obligation row records that route as the BEDC consumer contract. Since every coordinate is read from $D,W,\lambda,M,H,C,P,N$, no open-cover family or host compactness witness supplies the factorization.
\end{proof}

\begin{theorem}[Radius mesh stability obligation row]
\label{thm:finite-lebesgue-number-radius-mesh-stability-row}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, every stored $\hsame$ transport preserves the positive radius ledger $\lambda$ only together with the displayed $\RationalBallUp$ rows and the $\DyadicMeshUp$ mesh-refinement rows. Thus radius transport is not a scalar transport separate from the rational-ball and mesh evidence that names it.
\end{theorem}
\begin{proof}
Project the radius coordinate from the carrier. It is located between the finite-window row and the mesh ledger, and its admissible readback is tied to the rational-ball rows of the dyadic cover.

Apply the radius transport and finite radius nonchoice obligations. They keep $\lambda$ attached to rational-ball readback and mesh refinement under every stored $\hsame$ row and replayed $\Cont$ route, so a transported radius remains part of the same finite packet.
\end{proof}

\begin{theorem}[Compact consumer boundary obligation row]
\label{thm:finite-lebesgue-number-compact-consumer-boundary-row}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives only the displayed dyadic finite-cover packet $D,W,\lambda,M,H,C,P,N$. The consumer may inspect the finite cover, finite-window row, positive radius ledger, mesh-refinement row, transports, continuations, provenance, and local naming, but receives no arbitrary open-cover family, host compactness theorem, or selected subcover coordinate.
\end{theorem}
\begin{proof}
Use the total-bounded handoff obligation. It identifies $D,W,\lambda,M,H,C,P,N$ as the exact packet delivered to total-bounded and compact-metric consumers.

The coverage and radius-mesh rows above keep finite-window reads and radius reads inside that packet. The non-escape row of the local NameCert obligations excludes open-cover compactness and arbitrary subcover selection, so the compact consumer boundary is precisely the displayed dyadic finite-cover packet.
\end{proof}

\begin{theorem}[Window-radius source lock]
\label{thm:finite-lebesgue-number-window-radius-source-lock}
For every accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the positive radius ledger $\lambda$ is locked to the same source packet as the finite-window row $W$. The lock is witnessed only through the displayed $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows carried by $D,W,\lambda,M,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier $L=(D,W,\lambda,M,H,C,P,N)$. The window row $W$ and radius ledger $\lambda$ occur in the same finite $\BHist$ packet, with $D$ and $M$ recording the dyadic cover and mesh rows that read them.

Apply \autoref{thm:finite-lebesgue-number-radius-mesh-stability-row}. It keeps $\lambda$ attached to the rational-ball rows and dyadic-mesh refinement rows under the stored $\hsame$ transports and replayed $\Cont$ routes.

Apply \autoref{thm:finite-lebesgue-number-obligation-coverage-row}. It routes every accepted finite-window read through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, the mesh row $M$, and the cover row $D$. Therefore the radius source cannot be read apart from the same displayed source packet.
\end{proof}

\begin{theorem}[Total-bounded consumer factorization]
\label{thm:finite-lebesgue-number-total-bounded-consumer-factorization}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$ factors through the displayed dyadic finite-cover packet before reading any compact route. The factorization first reads $\DyadicCoverUp$ and $\FiniteWindowEnvelopeUp$, then reads $\RationalBallUp$ and $\DyadicMeshUp$, then reads $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, and finally replays only the carried $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-lebesgue-number-compact-consumer-boundary-row}. It identifies $D,W,\lambda,M,H,C,P,N$ as the exact packet delivered to total-bounded and compact-metric consumers.

Use \autoref{thm:finite-lebesgue-number-window-radius-source-lock}. The radius ledger and finite-window reads share the same dyadic source packet, so the consumer cannot detach $\lambda$ from $W$, $D$, or $M$.

Use \autoref{thm:finite-lebesgue-number-total-bounded-handoff}. The consumer-facing order is exhausted by the displayed carrier rows and their $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support, so the compact read factors through the finite dyadic packet.
\end{proof}

\begin{theorem}[Open-cover refusal boundary]
\label{thm:finite-lebesgue-number-open-cover-refusal-boundary}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, any request for an arbitrary open-cover family, a selected subcover, host compactness, or open-cover compactness is refused by the carrier boundary. The accepted request surface is only the finite route through $\DyadicCoverUp$, $\FiniteWindowEnvelopeUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Read the non-escape row of \autoref{thm:finite-lebesgue-number-namecert-obligations}. It excludes arbitrary open families, open-cover compactness, host compactness, and selected subcover coordinates from the carrier.

The compact consumer boundary theorem then identifies the only admitted consumer packet as $D,W,\lambda,M,H,C,P,N$. The total-bounded factorization theorem above keeps every compact route inside the finite dyadic cover, window, radius, mesh, stream, regular-rational, real, transport, replay, provenance, and naming rows.

Thus an open-cover request asks for data absent from the carrier. It is refused as a boundary crossing rather than answered by a hidden compactness principle.
\end{proof}

\begin{definition}[Finite Lebesgue number root coverage ledger]
\label{def:finite-lebesgue-number-root-coverage-ledger}
For an accepted $\FiniteLebesgueNumberUp$ carrier $L=(D,W,\lambda,M,H,C,P,N)$, the root coverage ledger is the finite $\BHist$ row
$$
\Lambda=(D,M,R,S,G,E,K,H,C,P,N)
$$
whose entries expose the $\DyadicCoverUp$ row $D$, $\DyadicMeshUp$ row $M$, $\RationalBallUp$ radius row $R$, $\StreamNameUp$ window row $S$, $\RegSeqRatUp$ source row $G$, $\RealUp$ endpoint row $E$, $\CompactMetricUp$ and $\CompactNetModulusSelectorUp$ consumer row $K$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. The ledger has no coordinate for arbitrary open-cover choice, selected subcover choice, or host compactness.
\end{definition}

\begin{theorem}[Finite Lebesgue number root dyadic radius obligation]
\label{thm:finite-lebesgue-number-root-dyadic-radius-obligation}
Every accepted root coverage ledger of \autoref{def:finite-lebesgue-number-root-coverage-ledger} must display the rational radius row $R$ as a $\RationalBallUp$ row read through the same finite $\DyadicCoverUp$ and $\DyadicMeshUp$ packet that supplies $D$ and $M$. The $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows $S,G,E$ may consume the radius only through the transported $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, not by a hidden open-cover compactness witness.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootDyadicRadiusObligation}
\begin{proof}
Project the ledger $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$. The radius row $R$ is listed between the dyadic cover and dyadic mesh rows, so its only source packet is the finite dyadic one.

Apply the radius-mesh stability row, \autoref{thm:finite-lebesgue-number-radius-mesh-stability-row}, and the window-radius source lock, \autoref{thm:finite-lebesgue-number-window-radius-source-lock}. Together they keep the rational-ball radius attached to $D,M$ under componentwise $\hsame$ transport and displayed $\Cont$ replay.

The stream, regular-rational, and real rows then read the transported finite packet. Since $\Lambda$ has no open-cover or selected-subcover coordinate, the radius obligation remains finite and nonchoice.
\end{proof}

\begin{theorem}[Finite Lebesgue number root compact consumer nonchoice]
\label{thm:finite-lebesgue-number-root-compact-consumer-nonchoice}
Every $\CompactMetricUp$ or $\CompactNetModulusSelectorUp$ consumer of an accepted root coverage ledger factors through the displayed $\DyadicCoverUp$, $\DyadicMeshUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows before it may read $K$. The consumer uses only the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the ledger and cannot request an arbitrary open cover or selected subcover.
\end{theorem}
\begin{proof}
Start from total-bounded consumer factorization, \autoref{thm:finite-lebesgue-number-total-bounded-consumer-factorization}. It routes every compact-metric consumer through the finite dyadic packet before any compact read is exposed.

Use the open-cover refusal boundary, \autoref{thm:finite-lebesgue-number-open-cover-refusal-boundary}. It blocks arbitrary open covers, host compactness, and selected subcover coordinates, leaving only the finite cover, mesh, radius, stream, regular-rational, real, transport, replay, provenance, and naming rows.

Thus $K$ is a consumer of the displayed finite ledger rather than a compactness selector outside it. The route is nonchoice because every consumed row is already present in $\Lambda$.
\end{proof}

\begin{theorem}[Finite Lebesgue number root window cover totality]
\label{thm:finite-lebesgue-number-root-window-cover-totality}
For every accepted root coverage ledger $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$, each window named by the $\StreamNameUp$ row $S$ and each regular-rational source named by the $\RegSeqRatUp$ row $G$ is covered by one of the finitely displayed $\RationalBallUp$ rows of $R$ over the $\DyadicCoverUp$ and $\DyadicMeshUp$ rows $D,M$. The $\RealUp$ endpoint row $E$ and compact-consumer row $K$ may read totality only through that finite window-cover route.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootWindowCoverTotality}
\begin{proof}
Read finite-window coverage exactness through \autoref{thm:finite-lebesgue-number-obligation-coverage-row}. It sends every accepted finite-window read through the displayed dyadic cover, mesh, stream, regular-rational, and real rows.

The root dyadic radius obligation above attaches each rational ball to the same $D,M$ source packet. Therefore the windows named by $S$ and sources named by $G$ are covered by listed rational-ball rows rather than by an external subcover.

Finally the compact consumer nonchoice theorem keeps $E$ and $K$ downstream of that same finite route. The totality claim is exactly the finite ledger totality, not an open-cover compactness assertion.
\end{proof}

\begin{theorem}[Finite Lebesgue number root unblock package]
\label{thm:finite-lebesgue-number-root-unblock-package}
The accepted root coverage ledger of \autoref{def:finite-lebesgue-number-root-coverage-ledger} forms a finite root-unblock package for $\FiniteLebesgueNumberUp$: the $\DyadicCoverUp$, $\DyadicMeshUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactMetricUp$, and $\CompactNetModulusSelectorUp$ rows are all exposed inside one $\BHist$ packet, preserved by $\hsame$, replayed by $\Cont$, sourced by $\Pkg$, and sealed by $\NameCert$. Consequently the later root consumer may target finite cover, radius, window totality, and compact-consumer obligations without relying on arbitrary open-cover compactness or choice.
\end{theorem}
\begin{proof}
Assemble the package from the root coverage ledger. The definition lists the dyadic cover, dyadic mesh, rational ball, stream, regular-rational, real endpoint, compact-metric, compact-net selector, transport, replay, provenance, and local naming rows in one finite $\BHist$ packet.

The dyadic radius obligation supplies the radius row over the same finite dyadic packet. The compact consumer nonchoice theorem keeps compact consumers inside the displayed finite rows. The window cover totality theorem then supplies totality for the StreamName and RegSeqRat windows through the listed rational-ball rows.

Repacking these three obligations with $H,C,P,N$ gives the finite root-unblock package. No step introduces open-cover compactness, selected subcover choice, host compactness, or a consumer row outside the displayed ledger.
\end{proof}

\begin{theorem}[Finite Lebesgue number selector-radius domain]
\label{thm:finite-lebesgue-number-selector-radius-domain}
The positive radius ledger consumed by $\CompactNetModulusSelectorUp$ is readable only through the displayed $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the accepted $\FiniteLebesgueNumberUp$ root coverage ledger. It has no separate open-cover compactness, selected-subcover, host-minimum, or choice coordinate.
\end{theorem}
\begin{proof}
Project the root coverage ledger $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$. The positive radius row is the rational-ball row $R$, and it is displayed with the dyadic cover and dyadic mesh rows $D,M$ before any compact-net selector reads $K$.

Use the root dyadic radius obligation and window-radius source lock. \autoref{thm:finite-lebesgue-number-root-dyadic-radius-obligation} keeps $R$ over the same $D,M$ packet, while \autoref{thm:finite-lebesgue-number-window-radius-source-lock} ties finite-window reads to the same dyadic source.

Finally attach $S,G,E,H,C,P,N$. The StreamName, RegSeqRat, Real, transport, replay, provenance, and local naming rows are the only rows that can carry the radius onward to $\CompactNetModulusSelectorUp$, so no hidden compactness or choice coordinate is available.
\end{proof}

\begin{theorem}[Finite Lebesgue number compact-net selector factorization]
\label{thm:finite-lebesgue-number-compactnet-selector-factorization}
Every $\CompactNetModulusSelectorUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ root coverage ledger factors through the root coverage ledger before reading its selector row. The factorization route is
$$
D,M,R,S,G,E,H,C,P,N \to K,
$$
so the selector receives finite cover, mesh, radius, stream, regular-rational, real endpoint, transport, replay, provenance, and local naming data before any compact-net selection occurs.
\end{theorem}
\begin{proof}
Begin with the root unblock package, \autoref{thm:finite-lebesgue-number-root-unblock-package}. It exposes the compact-net selector row inside the same finite $\BHist$ packet as the dyadic cover, mesh, radius, stream, regular-rational, and real rows.

Next use root compact consumer nonchoice and total-bounded consumer factorization. \autoref{thm:finite-lebesgue-number-root-compact-consumer-nonchoice} and \autoref{thm:finite-lebesgue-number-total-bounded-consumer-factorization} both route compact consumers through the finite dyadic packet before any compact read is exposed.

The selector-radius domain theorem supplies the remaining radius constraint. Since $R$ is readable only through the displayed dyadic and transport rows, the selector row $K$ factors through the root coverage ledger rather than an external subcover selector.
\end{proof}

\begin{theorem}[Finite Lebesgue number uniform-modulus radius exhaustion]
\label{thm:finite-lebesgue-number-uniform-modulus-radius-exhaustion}
Every $\UniformModulusUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ packet receives only the finite Lebesgue-number radius packet carried by the displayed root coverage ledger. It receives no open-cover compactness, no selected subcover, no host minimum, and no countable or finite choice coordinate beyond the finite rows already named by $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
First read the selector-radius domain theorem. It identifies the positive radius ledger as the rational-ball row over the finite dyadic cover and mesh packet, transported only by the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Apply compact-net selector factorization. Any compact-net route to a modulus selector must pass through $D,M,R,S,G,E,H,C,P,N$ before it reaches $K$, so the modulus-facing consumer receives a finite packet rather than an open-cover object.

Finally use the open-cover refusal boundary, \autoref{thm:finite-lebesgue-number-open-cover-refusal-boundary}. It blocks arbitrary open families, host compactness, and selected-subcover coordinates, leaving $\UniformModulusUp$ with only the finite Lebesgue-number radius packet.
\end{proof}

\begin{definition}[Finite Lebesgue-number radius lower-bound fold]
\label{def:finite-lebesgue-number-radius-lower-bound-fold}
For an accepted $\FiniteLebesgueNumberUp$ root coverage ledger
$$
\Lambda=(D,M,R,S,G,E,K,H,C,P,N),
$$
the radius lower-bound fold is the finite $\BHist$ packet
$$
F_\Lambda=(D,R,M,S,G,E,K,H,C,P,N)
$$
whose read order first displays the $\DyadicCoverUp$ row $D$, then the $\RationalBallUp$ radius row $R$, then the $\DyadicMeshUp$ row $M$, and then the $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactNetModulusSelectorUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The fold is a finite lower-bound packet for the displayed radius rows only: it has no coordinate for a host minimum, arbitrary open-cover compactness, selected subcover choice, quotient equality, or external modulus selector.
\end{definition}

\begin{theorem}[Finite Lebesgue-number cover-shrinkage stability]
\label{thm:finite-lebesgue-number-cover-shrinkage-stability}
Let $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$ be an accepted $\FiniteLebesgueNumberUp$ root coverage ledger. Shrinking each displayed cover cell along the folded positive radius packet $F_\Lambda$ preserves the same $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route. In particular, every shrunken-cell read remains a read through the folded finite lower-bound packet and not through an open-cover compactness theorem, selected subcover, host minimum, quotient equality, or choice coordinate.
\end{theorem}
\begin{proof}
Project the root coverage ledger of \autoref{def:finite-lebesgue-number-root-coverage-ledger}. Its rows already place $D,R,M,S,G,E,K,H,C,P,N$ in one finite $\BHist$ packet, and the lower-bound fold only changes the read order so the rational-ball radius is inspected before the mesh row.

Use the selector-radius domain theorem, \autoref{thm:finite-lebesgue-number-selector-radius-domain}. It says the positive radius ledger is readable only through the displayed dyadic cover, rational-ball, dyadic mesh, stream, regular-rational, real, transport, replay, provenance, and naming rows.

Apply compact-net selector factorization and uniform-modulus radius exhaustion. \autoref{thm:finite-lebesgue-number-compactnet-selector-factorization} keeps the selector downstream of the folded packet, and \autoref{thm:finite-lebesgue-number-uniform-modulus-radius-exhaustion} prevents a modulus consumer from replacing that radius with open-cover compactness or a selected subcover.

Thus cover-cell shrinkage is stable under the same displayed transports and replays. The shrinkage endpoint is the folded finite lower-bound packet, not a host minimum or external equality coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue-number UniformModulus consumer exactness]
\label{thm:finite-lebesgue-number-uniform-modulus-consumer-exactness}
Every $\UniformModulusUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ root coverage ledger factors through the radius lower-bound fold $F_\Lambda$. The consumer receives exactly the finite radius packet
$$
D,R,M,S,G,E,H,C,P,N \to K
$$
carried by $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it receives no open-cover compactness theorem, selected subcover, host minimum, quotient equality, choice coordinate, or external modulus row.
\end{theorem}
\begin{proof}
Begin with the root coverage ledger. By \autoref{def:finite-lebesgue-number-root-coverage-ledger}, every candidate consumer row is already displayed inside $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$, and \autoref{def:finite-lebesgue-number-radius-lower-bound-fold} repacks those rows as the finite lower-bound packet $F_\Lambda$.

Apply \autoref{thm:finite-lebesgue-number-selector-radius-domain}. It identifies $R$ as the positive radius ledger over the displayed $D,M$ dyadic packet and keeps all later reads inside $S,G,E,H,C,P,N$.

Next apply \autoref{thm:finite-lebesgue-number-compactnet-selector-factorization} and \autoref{thm:finite-lebesgue-number-uniform-modulus-radius-exhaustion}. The first theorem routes $K$ through the finite packet before any selector read, and the second theorem states that a $\UniformModulusUp$ consumer receives only the finite Lebesgue-number radius packet.

Finally use cover-shrinkage stability. It shows that shrinking cover cells to the folded positive radius remains stable under the same displayed transport and replay rows, so the consumer receives exactly $D,R,M,S,G,E,H,C,P,N \to K$ and no open-cover compactness, selected-subcover, host-minimum, quotient-equality, or choice coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue number radius-modulus transport scope]
\label{thm:finite-lebesgue-number-radius-modulus-transport-scope}
In every accepted $\FiniteLebesgueNumberUp$ root coverage ledger, the positive radius ledger is transported toward a modulus only together with the displayed $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Thus the radius-to-modulus route has no separate carrier for a compact minimum, an open-cover selector, or a choice coordinate outside the finite dyadic-cover packet.
\end{theorem}
\begin{proof}
Project the accepted ledger $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$. The selector-radius domain theorem identifies $R$ as the positive rational-ball radius row over the displayed dyadic cover and mesh rows $D,M$.

Apply the compact-net selector factorization theorem and the uniform-modulus radius exhaustion theorem. They force every modulus-facing consumer to pass through $D,M,R,S,G,E,H,C,P,N$ before any selector row can be read.

The remaining rows are exactly the StreamName, RegSeqRat, Real, transport, replay, provenance, and NameCert rows already named in the ledger. Since no other row is present, radius-modulus transport is scoped by the displayed finite packet.
\end{proof}

\begin{theorem}[Finite Lebesgue number open-phase root package]
\label{thm:finite-lebesgue-number-open-phase-root-package}
Every accepted $\FiniteLebesgueNumberUp$ root coverage ledger presents its finite Lebesgue-number root surface as the finite-window route
$$
D,M,R,S,G,E,H,C,P,N
$$
inside one $\BHist$ packet. The route is anchored by $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, starts from the displayed $\DyadicCoverUp$ and $\DyadicMeshUp$ evidence, and transports the positive $\RationalBallUp$ radius through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ consumers without exposing open-cover compactness, a selected subcover, a host minimum, quotient equality, or a choice coordinate.
\end{theorem}
\begin{proof}
Read the dyadic-cover handoff and the root coverage ledger. They display the cover, mesh, rational-radius, stream, regular-rational, real, transport, replay, provenance, and local naming rows in one finite $\BHist$ packet.

Apply the finite-window coverage exactness, root compact consumer nonchoice, and radius-modulus transport scope rows. Together they route every root-surface read through $D,M,R,S,G,E,H,C,P,N$ before any compact or uniform consumer can inspect the packet.

The open-cover refusal boundary supplies the negative side of the package. Since no arbitrary open family, selected subcover, host compactness minimum, quotient equality, or external selector row is present, the root surface is precisely the displayed finite-window route.
\end{proof}

\begin{theorem}[Finite Lebesgue number compact cover-selection row]
\label{thm:finite-lebesgue-number-compact-cover-selection-row}
Every $\CompactMetricUp$ cover-selection consumer of an accepted $\FiniteLebesgueNumberUp$ packet consumes the dyadic cover row $D$, total-bounded finite-window rows, dyadic mesh row $M$, rational radius row $R$, and the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ ledger before any compact read. Thus compact cover selection is a finite-route read from $\DyadicCoverUp$, $\DyadicMeshUp$, $\TotallyBoundedUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ data, not a read from open-cover compactness or a choice-like selected subcover.
\end{theorem}
\begin{proof}
Start from the finite-window route of \autoref{thm:finite-lebesgue-number-open-phase-root-package}. It places the dyadic cover, mesh, radius, stream, regular-rational, real, transport, replay, provenance, and naming rows before the compact consumer.

Use the total-bounded consumer factorization and compact-net selector factorization rows. These factor the compact-metric read through the displayed finite cover and mesh packet, so the compact route consumes the finite dyadic data already present in the ledger.

Finally apply the open-cover refusal boundary. The compact consumer therefore has no coordinate from which to read an arbitrary open cover, a selected subcover, or a compactness minimum; it receives only the finite cover-selection row anchored in $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{proof}

\begin{theorem}[Finite Lebesgue number ContinuousMap uniform route row]
\label{thm:finite-lebesgue-number-continuousmap-uniform-route-row}
Every $\ContinuousMapUp$ or $\UniformModulusUp$ consumer reading an accepted $\FiniteLebesgueNumberUp$ packet may read only the explicit radius ledger and the compact-net route
$$
D,M,R,S,G,E,H,C,P,N \to K.
$$
The consumer may replay $\Cont$ and transport along $\hsame$ inside the stored $\BHist$ packet, and may cite the displayed $\Pkg$ and $\NameCert$ rows, but it cannot replace that route by an external continuity modulus, open-cover compactness, selected subcover, host minimum, quotient equality, or choice coordinate.
\end{theorem}
\begin{proof}
Begin with radius-modulus transport scope. It already restricts the positive radius ledger to the displayed dyadic cover, mesh, stream, regular-rational, real, transport, replay, provenance, and naming rows.

Attach the compact-net selector factorization and UniformModulus consumer exactness rows. They place $K$ downstream of $D,M,R,S,G,E,H,C,P,N$ and identify the modulus-facing packet as the radius lower-bound fold rather than an independent continuity object.

The replay row for $\ContinuousMapUp$ is therefore a consumer of the stored finite route. It can read $\Cont$ only as part of the same $\BHist$ packet, so the uniform route remains the explicit radius ledger and compact-net route, with no outside open-cover or choice coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue number compact uniform handoff scope]
\label{thm:finite-lebesgue-number-compact-uniform-handoff-scope}
Every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ packet factors through the same displayed finite dyadic-cover packet before receiving compact or uniform-continuity data. The handoff route is the finite row family
$$
D,M,R,S,G,E,H,C,P,N \to K,
$$
with $D$ from $\DyadicCoverUp$, $M$ from $\DyadicMeshUp$, $R$ from $\RationalBallUp$, $S$ from $\StreamNameUp$, $G$ from $\RegSeqRatUp$, $E$ from $\RealUp$, and $H,C,P,N$ from $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Start with the root compact consumer nonchoice theorem. It sends compact-metric and compact-net consumers through the finite dyadic cover, mesh, radius, stream, regular-rational, real, transport, replay, provenance, and naming rows before any compact read is exposed.

Next use compact-net selector factorization. The displayed route $D,M,R,S,G,E,H,C,P,N \to K$ makes the selector row downstream of the same finite packet rather than a source of independent compactness.

Finally apply uniform-modulus radius exhaustion. The uniform-modulus consumer receives only the radius packet carried by those same rows, so compactness and uniform continuity meet at the displayed handoff and nowhere outside it.
\end{proof}

\begin{theorem}[Finite Lebesgue number scoped closure package]
\label{thm:finite-lebesgue-number-scoped-closure-package}
The finite dyadic-cover obligations displayed in the $\FiniteLebesgueNumberUp$ root coverage ledger form a scoped closure package: the root unblock package, selector-radius domain, compact-net selector factorization, uniform-modulus radius exhaustion, radius lower-bound fold, cover-shrinkage stability, UniformModulus consumer exactness, radius-modulus transport scope, and compact uniform handoff scope all use the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet. Hence the chapter closes the finite Lebesgue-number scope for explicit dyadic-cover radius transport and compact-to-uniform handoff.
\end{theorem}
\begin{proof}
First assemble the existing root route. The root unblock package exposes the dyadic cover, dyadic mesh, rational radius, stream, regular-rational, real endpoint, compact-metric, compact-net selector, transport, replay, provenance, and local naming rows in one finite packet.

The selector-radius domain, compact-net selector factorization, and uniform-modulus radius exhaustion theorems then route the positive radius from that packet toward selector and uniform-modulus consumers. No step introduces an external open cover, selected subcover, host minimum, or choice coordinate.

Insert the radius lower-bound fold and cover-shrinkage stability rows. They turn the displayed rational-ball radius into the finite lower-bound packet and keep cover shrinkage inside the same transported and replayed rows.

Add UniformModulus consumer exactness, radius-modulus transport scope, and compact uniform handoff scope. These rows state that both the modulus transport and the compact-to-uniform handoff consume the same displayed dyadic-cover packet, so the finite Lebesgue-number scope is closed at the displayed rows.
\end{proof}

\begin{theorem}[Finite Lebesgue number radius-cover monotone readback]
\label{thm:finite-lebesgue-number-radius-cover-monotone-readback}
In every accepted $\FiniteLebesgueNumberUp$ root coverage ledger $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$, the positive radius row $R$ is readable only after the displayed $\DyadicCoverUp$ row $D$ and the $\RationalBallUp$ readback rows attached to $D$ have been exposed. Any $\hsame$ transport in $H$ or $\Cont$ replay in $C$ may extend the read toward $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactMetricUp$, and $\CompactNetModulusSelectorUp$ consumers, but it cannot detach $R$ from the finite cover row or reverse the finite read order.
\end{theorem}
\begin{proof}
Start with the carrier and root coverage ledger. The carrier of \autoref{def:finite-lebesgue-number-carrier} places the finite cover, radius ledger, mesh ledger, transport, replay, provenance, and local naming rows in one packet, while \autoref{def:finite-lebesgue-number-root-coverage-ledger} displays them as $\Lambda=(D,M,R,S,G,E,K,H,C,P,N)$.

Use the NameCert obligations, radius transport, and finite-radius nonchoice rows. \autoref{thm:finite-lebesgue-number-namecert-obligations}, \autoref{thm:finite-lebesgue-number-radius-transport}, and \autoref{thm:finite-lebesgue-number-finite-radius-nonchoice} require every radius read to pass through the rational-ball rows tied to the displayed dyadic cover and mesh evidence.

Next apply the selector-radius domain and radius-modulus transport scope. They keep $R$ downstream of $D$ and upstream of every compact-net or modulus-facing consumer, with $H$ and $C$ acting only as stored transport and replay rows.

The readback is therefore monotone in the finite ledger order: transport and replay can carry the displayed radius to later consumers, but cannot create an earlier host radius, open-cover compactness row, selected subcover, or external modulus function.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRadiusCoverMonotoneReadback}

\begin{theorem}[Finite Lebesgue number mesh-refinement cover exhaustion]
\label{thm:finite-lebesgue-number-mesh-refinement-cover-exhaustion}
For every accepted $\FiniteLebesgueNumberUp$ root coverage ledger, each mesh-refinement read from $\DyadicMeshUp$ exhausts into a named cover cell through the displayed $\DyadicCoverUp$, $\RationalBallUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The exhaustion is finite: no mesh cell may request an arbitrary open cover, a selected subcover, host compactness, quotient equality, or a cover-cell selector outside the ledger.
\end{theorem}
\begin{proof}
Begin with finite-window coverage exactness and the obligation coverage row. \autoref{thm:finite-lebesgue-number-window-coverage-exactness} and \autoref{thm:finite-lebesgue-number-obligation-coverage-row} send every accepted window read through a $\StreamNameUp$ row, a $\RegSeqRatUp$ approximation row, a $\RealUp$ row, a mesh cell, and a named dyadic cover cell.

Attach the mesh-refinement nonchoice and radius-mesh stability rows. \autoref{thm:finite-lebesgue-number-mesh-refinement-nonchoice} keeps the mesh-to-cover handoff stable under the stored $\hsame$ transports and replayed $\Cont$ routes, while \autoref{thm:finite-lebesgue-number-radius-mesh-stability-row} keeps the mesh evidence tied to the positive rational-ball radius readback.

Now read the root window cover totality theorem and the root unblock package. They place the StreamName, RegSeqRat, Real, mesh, cover, transport, replay, provenance, and local naming rows in the same finite $\BHist$ packet before compact consumers inspect the ledger.

Thus every mesh-refinement read exhausts into a named cover cell already present in the displayed packet. Since the packet has no coordinate for open-cover compactness, arbitrary subcover selection, host compactness, quotient equality, or an external cell selector, the exhaustion is nonchoice.
\end{proof}

\begin{theorem}[Finite Lebesgue number compact-route dyadic modulus package]
\label{thm:finite-lebesgue-number-compact-route-dyadic-modulus-package}
The compact route from an accepted $\FiniteLebesgueNumberUp$ ledger to $\CompactMetricUp$ and $\CompactNetModulusSelectorUp$ consumers is exactly the finite dyadic modulus packet
$$
D,R,M,S,G,E,H,C,P,N \to K .
$$
It packages the displayed $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows for compact consumers, and it exports no open-cover compactness theorem, host compactness witness, arbitrary subcover selector, quotient equality, or external modulus function.
\end{theorem}
\begin{proof}
Start from the compact consumer route and compact consumer nonchoice boundary. \autoref{thm:finite-lebesgue-number-compact-consumer-route} and \autoref{thm:finite-lebesgue-number-compact-consumer-nonchoice-boundary} identify the compact-facing data as the displayed finite carrier and exclude open-cover compactness, host compactness, arbitrary subcover choice, and external selectors.

Use the root compact consumer nonchoice theorem with compact-net selector factorization. \autoref{thm:finite-lebesgue-number-root-compact-consumer-nonchoice} sends both compact-metric and compact-net consumers through $D,M,R,S,G,E,H,C,P,N$, and \autoref{thm:finite-lebesgue-number-compactnet-selector-factorization} records $K$ as downstream of that finite packet.

Apply radius-cover monotone readback and mesh-refinement cover exhaustion. The first keeps the positive radius row readable only after the displayed cover and rational-ball rows, and the second exhausts every mesh-refinement read into a named cover cell through the StreamName, RegSeqRat, Real, transport, replay, provenance, and naming rows.

Finally add the compact uniform handoff scope and scoped closure package. These results state that compact and uniform consumers meet at the same finite dyadic-cover packet, so the compact route is precisely $D,R,M,S,G,E,H,C,P,N \to K$ and not an open-cover compactness or choice-sensitive subcover route.
\end{proof}

\begin{theorem}[Finite Lebesgue number public compact-uniform export]
\label{thm:finite-lebesgue-number-public-compact-uniform-export}
The public $\FiniteLebesgueNumberUp$ export for compact-uniform consumers is exactly the finite packet
$$
D,R,M,S,G,E,H,C,P,N \to K .
$$
Here $D$ is the displayed $\DyadicCoverUp$ row, $R$ the $\RationalBallUp$ radius readback, $M$ the $\DyadicMeshUp$ refinement ledger, $S$ the $\StreamNameUp$ row, $G$ the $\RegSeqRatUp$ row, $E$ the $\RealUp$ row, $H,C,P,N$ the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and $K$ the compact-net selector handoff read by $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumers. The export has no coordinate for open-cover compactness, selected subcovers, host minima, quotient equality, choice, or external modulus functions.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPublicCompactUniformExport}
\begin{proof}
Begin with the scoped closure package. \autoref{thm:finite-lebesgue-number-scoped-closure-package} already binds the root unblock package, selector-radius domain, compact-net selector factorization, uniform-modulus radius exhaustion, lower-bound fold, cover-shrinkage stability, consumer exactness, and compact uniform handoff to the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.

Next attach radius-cover monotone readback and mesh-refinement cover exhaustion. \autoref{thm:finite-lebesgue-number-radius-cover-monotone-readback} keeps $R$ downstream of the displayed cover and rational-ball rows, while \autoref{thm:finite-lebesgue-number-mesh-refinement-cover-exhaustion} sends every mesh read into a named cover cell through $D,R,M,S,G,E,H,C,P,N$.

Finally apply the compact-route dyadic modulus package. \autoref{thm:finite-lebesgue-number-compact-route-dyadic-modulus-package} identifies the compact-facing route as $D,R,M,S,G,E,H,C,P,N \to K$. Since the preceding results place both compact and uniform-modulus reads inside that same finite route, the public export is the displayed packet and nothing outside it: no open-cover compactness, selected subcover, host minimum, quotient equality, choice, or external modulus function is exported.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact-radius bridge]
\label{thm:finite-lebesgue-number-compact-radius-bridge}
Every $\CompactMetricUp$ or $\CompactNetModulusSelectorUp$ consumer of an accepted $\FiniteLebesgueNumberUp$ carrier receives the positive finite-radius ledger only through the displayed route
$$
D,W,\lambda,M,H,C,P,N .
$$
The bridge route passes through $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before the compact or compact-net consumer reads the radius ledger. It exports no open-cover compactness, selected subcover, host minimum, quotient equality, or external radius selector.
\end{theorem}
\begin{proof}
Start with radius transport and mesh-refinement nonchoice. \autoref{thm:finite-lebesgue-number-radius-transport} keeps $\lambda$ tied to the displayed rational-ball readback, and \autoref{thm:finite-lebesgue-number-mesh-refinement-nonchoice} keeps the mesh-to-cover route inside the same stored transport and replay rows.

Next use the total-bounded handoff and compact-uniform selector handoff. \autoref{thm:finite-lebesgue-number-total-bounded-handoff} identifies $D,W,\lambda,M,H,C,P,N$ as the compact-facing finite packet, while \autoref{thm:finite-lebesgue-number-compact-uniform-selector-handoff} sends the same positive radius ledger to compact-net and uniform consumers.

Finally apply the L10 source-lock. \autoref{thm:finite-lebesgue-number-l10-source-lock} forces the compact-radius read through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicMeshUp$, and $\DyadicCoverUp$ before any consumer inspects the ledger. Hence the bridge is exactly the displayed dyadic finite-radius route and has no open-cover or choice coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue-number uniform-modulus radius scope]
\label{thm:finite-lebesgue-number-uniform-modulus-radius-scope}
Every $\UniformModulusUp$ handoff from an accepted $\FiniteLebesgueNumberUp$ carrier may read only the displayed positive finite-radius row in $D,W,\lambda,M,H,C,P,N$. The handoff cannot add open-cover compactness, a selected subcover, a host minimum, $\RealUp$ completeness, quotient equality, or an external modulus function to the radius scope.
\end{theorem}
\begin{proof}
Begin with the compact-uniform selector handoff. It already places the uniform-modulus read downstream of the positive radius ledger carried by the displayed dyadic cover, finite-window, rational-ball, mesh, transport, replay, provenance, and local naming rows.

Use total-bounded handoff and window-radius ledger coherence. The total-bounded handoff fixes the compact-facing packet as $D,W,\lambda,M,H,C,P,N$, and window-radius ledger coherence prevents a window read from acquiring a separate positive radius outside the same packet.

The compact consumer nonchoice boundary supplies the negative side. It excludes open-cover compactness, selected subcovers, host minima, quotient equality, and external selectors from the compact route, so the uniform-modulus handoff inherits only the displayed positive finite-radius row and not a stronger compactness or completeness principle.
\end{proof}

\begin{theorem}[Finite Lebesgue-number dyadic-cover Real route]
\label{thm:finite-lebesgue-number-dyadic-cover-real-route}
Every accepted $\FiniteLebesgueNumberUp$ finite-window read reaches $\RealUp$ only through $\StreamNameUp$ and $\RegSeqRatUp$ before mesh and cover-cell readback. The resulting dyadic-cover route then continues through $\DyadicMeshUp$, $\DyadicCoverUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$; no host real representative, open cover, selected subcover, or arbitrary cover-cell selector supplies the endpoint.
\end{theorem}
\begin{proof}
Start from finite-window coverage exactness and stream-regular window order. These results force each finite-window read to pass first through $\StreamNameUp$ and $\RegSeqRatUp$, then through $\RealUp$, before any mesh cell or dyadic cover cell is read.

Apply the Real source nonchoice boundary. It rules out host real equality, arbitrary point selection, open-cover compactness, subcover choice, and external real representatives as sources for the $\RealUp$ row.

Finally use cover-cell readback totality. The mesh and cover-cell endpoint is packaged by the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so the Real route reaches the dyadic cover only through the stated stream and regular-rational sources.
\end{proof}

\begin{theorem}[Finite Lebesgue-number source-chain admission]
\label{thm:finite-lebesgue-number-source-chain-admission}
An accepted $\FiniteLebesgueNumberUp$ route is admitted only after the displayed $\DyadicCoverUp$, $\RationalBallUp$, and $\DyadicMeshUp$ rows pass through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ source rows, all carried by the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberSourceChainAdmission}
\begin{proof}
Use finite-window coverage exactness to place every finite read inside the displayed window packet.

Then apply \autoref{thm:finite-lebesgue-number-dyadic-cover-real-route}. It forces the source chain through $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before any dyadic mesh or cover-cell endpoint is admitted.

Finally use \autoref{thm:finite-lebesgue-number-compact-route-dyadic-modulus-package}. The compact-facing package is exactly the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route, so admission cannot bypass the displayed L10 source rows.
\end{proof}

\begin{theorem}[Finite Lebesgue-number ledger transport]
\label{thm:finite-lebesgue-number-ledger-transport}
For every accepted $\FiniteLebesgueNumberUp$ carrier, $\hsame$ transport preserves the positive radius ledger together with the dyadic cover, mesh, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows. The radius is never transported as a detached scalar outside the displayed finite source packet.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-lebesgue-number-radius-mesh-stability-row}. It keeps the positive rational-ball read attached to the dyadic mesh evidence under stored $\hsame$ transport.

Next use \autoref{thm:finite-lebesgue-number-window-radius-source-lock}. The finite-window and radius ledgers share the same dyadic source packet, including the stream, regular-rational, and Real rows.

Apply \autoref{thm:finite-lebesgue-number-radius-cover-monotone-readback}. Every transported radius read remains downstream of the displayed cover and rational-ball rows, so no scalar radius separates from the finite ledger.
\end{proof}

\begin{theorem}[Finite Lebesgue-number consumer nonescape triad]
\label{thm:finite-lebesgue-number-consumer-nonescape-triad}
The $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumers of an accepted $\FiniteLebesgueNumberUp$ carrier receive only the displayed finite route. They cannot import open-cover compactness, a host minimum, a selected subcover, quotient equality, choice, or external modulus data.
\end{theorem}
\begin{proof}
Use \autoref{thm:finite-lebesgue-number-compact-consumer-boundary-row} to fix the compact and compact-net consumer boundary at the displayed finite packet.

Then apply \autoref{thm:finite-lebesgue-number-compact-uniform-handoff-scope}. The uniform-modulus handoff reads the same radius and cover route rather than a stronger compactness principle.

Finally use \autoref{thm:finite-lebesgue-number-public-compact-uniform-export}. The public export has no coordinate for open-cover compactness, host minima, selected subcovers, quotient equality, choice, or external modulus data, so the three consumers cannot escape the finite route.
\end{proof}
