\begin{theorem}[Finite Lebesgue-number open Phase root-unblock radius coverage]
\label{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage}
Every accepted $\FiniteLebesgueNumberUp$ root radius read exported to the open Phase Real route factors through the finite radius-unblock packet
$$
D,B,M,E,S,Q,R,H,C,P,N
$$
where $D$ is the displayed $\DyadicCoverUp$ cover row, $B$ is the $\RationalBallUp$ positive-radius row, $M$ is the $\DyadicMeshUp$ mesh row, $E$ is the $\DyadicRatCoreUp$ source face, $S,Q,R$ are the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces, and the surrounding $\BHist$ records $H,C,P,N$ as the $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and compatible local $\NameCert$ rows. Thus the root-unblock obligation exposed to compact-uniform consumers is a finite BEDC packet over these rows, not a host-side radius source.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseRootUnblockRadiusCoverage}
\begin{proof}
Start with the root radius-window surface. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} identifies the positive radius and finite window through the dyadic cover, rational-ball radius, dyadic mesh, stream-name, regular-rational, Real, history, transport, replay, provenance, and naming rows.

Next attach the Phase Real source route. \autoref{thm:finite-lebesgue-number-phase-real-source-lock} forces each public radius read through the same dyadic, stream, regular-rational, and Real rows before a consumer can inspect it, while \autoref{thm:finite-lebesgue-number-real-phase-coverage-export} adds the $\DyadicRatCoreUp$ face to the compact, compact-net, continuous-map, and uniform-modulus export.

Finally read the exit and consumer ledgers. \autoref{thm:finite-lebesgue-number-root-unblock-exit-triad} gives the open Phase root-unblock exit surface, and \autoref{thm:finite-lebesgue-number-phase-real-radius-consumer-exhaustion} exhausts the consumer-visible radius source by the same finite rows. The displayed packet therefore covers every accepted root radius read exported to the open Phase Real route.
\end{proof}

\begin{theorem}[Finite Lebesgue-number open Phase root-unblock choice refusal]
\label{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal}
The open Phase root-unblock obligation packet for $\FiniteLebesgueNumberUp$ exports no open-cover compactness principle, selected subcover, host minimum, quotient stream equality, countable choice coordinate, detached $\RealUp$ completeness row, or external modulus row. Any admitted compact, continuous, totally bounded, or uniform radius use must be read from the finite dyadic, four-face Real, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet of \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage}.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseRootUnblockChoiceRefusal}
\begin{proof}
Read the positive side from the coverage theorem. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} leaves only the dyadic cover, rational-ball radius, dyadic mesh, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and BEDC support rows available to the open Phase root-unblock route.

The source and exit theorems supply the negative side. \autoref{thm:finite-lebesgue-number-phase-real-source-lock} prevents the source read from being replaced by an outside compactness or completeness primitive, and \autoref{thm:finite-lebesgue-number-root-unblock-exit-triad} states that the exit surface supplies no host Real equality, open-cover compactness, selected subcover, selected limit, detached completeness primitive, or external modulus data.

The consumer ledger closes the refusal at the endpoints. \autoref{thm:finite-lebesgue-number-phase-real-radius-consumer-exhaustion} removes open-cover compactness, host minima, selected subcovers, quotient stream equality, selected limits, countable choice, metric-completeness data, and detached $\RealUp$ completeness from compact, continuous, and uniform reads. The same finite packet is the only admitted source, so none of the listed outside rows can be exported.
\end{proof}

\begin{theorem}[Finite Lebesgue-number open Phase root-unblock consumer readback]
\label{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback}
The $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, and $\UniformModulusUp$ consumers downstream of an accepted $\FiniteLebesgueNumberUp$ open Phase root-unblock route read the same finite packet. Their visible radius source is exactly the shared $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route, with no consumer-specific radius source added at the endpoint.
\end{theorem}
\begin{proof}
First identify the shared source. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} factors every accepted root radius read through the finite dyadic and four-face Real packet, and \autoref{thm:finite-lebesgue-number-root-unblock-exit-triad} presents that packet as the root-unblock exit surface for compact-uniform consumers.

Next pass through Real-phase coverage. \autoref{thm:finite-lebesgue-number-real-phase-coverage-export} routes compact, compact-net, continuous-map, and uniform-modulus endpoints through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ together with the finite carrier rows. \autoref{thm:finite-lebesgue-number-phase-real-radius-consumer-exhaustion} then states that every compact, continuous, or uniform radius read is exhausted by the displayed dyadic, four-face Real, endpoint, history, transport, replay, provenance, and naming rows.

Finally compare the endpoint consumers. The $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, and $\UniformModulusUp$ rows have no coordinate outside the packet by \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal}. Since each endpoint reads through the same source rows and the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support, their consumer-visible radius source is the same finite packet.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseRootUnblockConsumerReadback}

\begin{theorem}[Finite Lebesgue-number root-unblock endpoint uniformity]
\label{thm:finite-lebesgue-number-root-unblock-endpoint-uniformity}
If two downstream endpoint reads for $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, or $\UniformModulusUp$ are accepted from the same $\FiniteLebesgueNumberUp$ open Phase root-unblock route, then their visible positive-radius source is one finite packet over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Conversely, any endpoint read displaying exactly that packet is an admissible consumer-visible radius read for the same route.
\end{theorem}
\begin{proof}
Start from the shared source assertion. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} says that every accepted root radius read exported to the open Phase Real route factors through the displayed dyadic, rational-ball, mesh, dyadic-rational, stream, regular-rational, Real, history, transport, replay, provenance, and naming rows.

The refusal theorem removes every possible endpoint-specific replacement. By \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal}, the route exports no consumer-specific radius source, open-cover compactness, selected subcover, host minimum, quotient equality, choice coordinate, external modulus, selected limit, or detached $\RealUp$-completeness row. Thus two accepted endpoint reads cannot differ by importing any outside radius witness.

Now compare the endpoint reads. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback} states that the $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, and $\UniformModulusUp$ consumers read exactly the same finite packet and add no endpoint-specific source. Hence any two accepted reads from the same root-unblock route have the same visible positive-radius source.

Conversely, an endpoint read that displays exactly the finite packet named above already presents the consumer-visible route required by \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback}. Since the refusal theorem excludes only outside rows and the displayed packet is precisely the covered source, such a read is admissible for the same open Phase root-unblock route.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootUnblockEndpointUniformity}

\begin{theorem}[Finite Lebesgue-number root-radius export exactness]
\label{thm:finite-lebesgue-number-root-radius-export-exactness}
An accepted $\FiniteLebesgueNumberUp$ root radius export is admissible exactly when it displays the finite packet over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The admissible export has no open-cover coordinate, selected-subcover coordinate, host minimum coordinate, or detached consumer radius source.
\end{theorem}
\begin{proof}
For the forward direction, start with an accepted root radius export. The carrier of \autoref{def:finite-lebesgue-number-carrier} fixes the local packet $D,W,\lambda,M,H,C,P,N$, and \autoref{thm:finite-lebesgue-number-namecert-obligations} names the carrier, classifier, radius-modulus stability, finite-window coverage, and non-escape rows that govern the packet.

Now pass to the open Phase route. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} factors every accepted root radius read through the displayed dyadic, rational-ball, mesh, four-face Real, history, transport, replay, provenance, and naming rows. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal} removes open-cover compactness, selected subcovers, host minima, quotient stream equality, detached completeness, and external modulus coordinates from that export.

For the reverse direction, suppose a radius export displays exactly those rows and no outside coordinate. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback} identifies that displayed packet as the consumer-visible radius source for the compact, continuous, totally bounded, and uniform endpoints. \autoref{thm:finite-lebesgue-number-root-unblock-endpoint-uniformity} then states that any endpoint read displaying exactly this finite packet is admissible for the same open Phase root-unblock route.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootRadiusExportExactness}

\begin{theorem}[Finite Lebesgue-number open Phase positive-radius stability]
\label{thm:finite-lebesgue-number-open-phase-positive-radius-stability}
Componentwise $\hsame$ transport and displayed $\Cont$ replay preserve the positive-radius row of an accepted $\FiniteLebesgueNumberUp$ open Phase root-unblock export only together with its $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows. In particular, the positive-radius row cannot be transported as a detached scalar outside the Phase Real and Completion packet.
\end{theorem}
\begin{proof}
Begin with the local carrier and NameCert rows. In \autoref{def:finite-lebesgue-number-carrier}, the positive ledger $\lambda$ is stored between the finite-window and mesh coordinates and is accompanied by the support rows $H,C,P,N$. The radius-modulus stability row of \autoref{thm:finite-lebesgue-number-namecert-obligations} preserves $\lambda$ only with the rational-ball and dyadic-mesh evidence that witnesses its refinement into the finite cover.

The open Phase coverage theorem extends this local stability to the root-unblock export. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} places the positive radius inside the same packet as $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Thus any componentwise $\hsame$ transport and displayed $\Cont$ replay is a transport of the displayed packet, not of an isolated radius coordinate.

Endpoint uniformity gives the stability test. By \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback} and \autoref{thm:finite-lebesgue-number-root-unblock-endpoint-uniformity}, every compact, continuous, totally bounded, or uniform endpoint reads the same finite packet. The choice-refusal theorem excludes a second radius source, so preserving the positive-radius row requires preserving the rational-ball, mesh, stream, regular-rational, and Real rows along with it.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhasePositiveRadiusStability}

\begin{theorem}[Finite Lebesgue-number L10 consumer radius exhaustion]
\label{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion}
Every $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, or $\UniformModulusUp$ consumer read of an accepted $\FiniteLebesgueNumberUp$ open Phase root-unblock route is exhausted by the same Phase Real and Completion packet over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. No consumer may add a consumer-specific radius witness to that route.
\end{theorem}
\begin{proof}
First identify the common packet. The carrier of \autoref{def:finite-lebesgue-number-carrier} and the NameCert obligations of \autoref{thm:finite-lebesgue-number-namecert-obligations} bind the finite radius ledger to the dyadic cover, finite-window, mesh, transport, replay, provenance, and naming rows.

Next route that packet through the open Phase root-unblock surface. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} supplies the Phase Real and Completion faces, while \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal} removes open-cover compactness, selected subcovers, host minima, quotient stream equality, detached completeness, and external modulus data.

Finally read the downstream consumers. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-consumer-readback} says that $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, and $\UniformModulusUp$ consume exactly the same finite packet. \autoref{thm:finite-lebesgue-number-root-unblock-endpoint-uniformity} identifies any endpoint display of that packet as the admissible read for the route, so a consumer-specific radius witness has no remaining coordinate to occupy.
\end{proof}

\begin{theorem}[Finite Lebesgue-number four-face radius exit coverage]
\label{thm:finite-lebesgue-number-four-face-radius-exit-coverage}
Every accepted $\FiniteLebesgueNumberUp$ root radius visible to a $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, compact-net, or $\UniformModulusUp$ consumer is exhausted by the four current open-phase source faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ together with the surrounding $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The visible exit package contains no radius source outside that four-face BEDC packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberFourFaceRadiusExitCoverage\_semantic\_name\_certificate}
\begin{proof}
Begin with root-unblock coverage. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} places every accepted root radius read inside the dyadic, rational-ball, mesh, four-face Real, history, transport, replay, provenance, and naming packet.

Now pass through the exact export and L10 endpoint route. \autoref{thm:finite-lebesgue-number-root-radius-export-exactness} identifies admissibility with displaying exactly that finite packet, and \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} says that compact, continuous, totally bounded, and uniform consumers cannot add a consumer-specific radius witness.

Finally attach the compact-net face to the same route. The sibling route of \autoref{thm:finite-lebesgue-number-l10-sibling-route} sends compact and compact-net reads through the finite-name chain before the positive radius is visible. Therefore every listed consumer reads the same four-face exit package and no outside radius source remains available.
\end{proof}

\begin{theorem}[Finite Lebesgue-number four-face radius exit determinacy]
\label{thm:finite-lebesgue-number-four-face-radius-exit-determinacy}
For accepted $\FiniteLebesgueNumberUp$ root-radius exits, componentwise agreement on the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows determines the downstream radius classifier seen by $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, compact-net, and $\UniformModulusUp$ consumers. Two such exits with the same displayed rows expose the same consumer-visible classifier.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberFourFaceRadiusExitDeterminacy}
\begin{proof}
First reduce the classifier to the root packet. By \autoref{thm:finite-lebesgue-number-root-radius-export-exactness}, an admissible root-radius export is exactly the finite packet over the four source faces and the support rows, with no independent compactness, minimum, subcover, or detached radius coordinate.

Next use endpoint uniformity. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} and \autoref{thm:finite-lebesgue-number-root-unblock-endpoint-uniformity} make every compact, continuous, totally bounded, and uniform endpoint read the same displayed packet. Componentwise $\hsame$ agreement and displayed $\Cont$ replay therefore carry the endpoint classifier without changing its source rows.

The compact-net route has no separate classifier channel. \autoref{thm:finite-lebesgue-number-l10-sibling-route} routes compact-net visibility through the same finite-name chain, while \autoref{thm:finite-lebesgue-number-regseq-streamname-nonescape} prevents the stream and regular-rational faces from being replaced by quotient stream equality, selected representatives, choice, or ambient completeness. Thus equal four-face rows determine the downstream radius classifier for every listed consumer.
\end{proof}

\begin{theorem}[Finite Lebesgue-number open Phase root-radius classifier totality]
\label{thm:finite-lebesgue-number-open-phase-root-radius-classifier-totality}
Every accepted $\FiniteLebesgueNumberUp$ root-radius exit visible to a $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, compact-net, or $\UniformModulusUp$ consumer has exactly one consumer-visible radius classifier. This classifier is determined by the shared $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the exit packet, and no endpoint can add a second classifier or detach the radius from the Phase Real and Completion packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseRootRadiusClassifierTotality}
\begin{proof}
Existence comes from the four-face exit surface. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-coverage} puts every accepted root radius visible to the listed consumers inside the displayed dyadic, four-face Real, history, transport, replay, provenance, and naming packet. \autoref{thm:finite-lebesgue-number-root-radius-export-exactness} identifies admissible export with that finite packet, so the visible classifier is read from the same rows rather than from an outside coordinate.

The endpoint ledger removes the remaining sources. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} exhausts compact, continuous, totally bounded, and uniform reads by the Phase Real and Completion packet, while \autoref{thm:finite-lebesgue-number-l10-sibling-route} sends compact-net visibility through the same finite-name route. Thus every accepted endpoint has a consumer-visible classifier carried by the shared packet.

Uniqueness follows from componentwise agreement. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-determinacy} says that agreement on the four source faces and the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows determines the downstream classifier for every listed consumer. A second classifier would either agree with those rows and therefore be the same classifier, or differ by an outside coordinate.

The outside-coordinate case is excluded by the refusal boundary. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal} and \autoref{thm:finite-lebesgue-number-four-face-radius-exit-nonescape} rule out host minima, selected subcovers, quotient stream equality, choice rows, selected limits, and detached $\RealUp$ completeness. Hence no endpoint can add a second classifier or detach the radius from the Phase Real and Completion packet.
\end{proof}

\begin{theorem}[Finite Lebesgue-number four-face radius exit nonescape]
\label{thm:finite-lebesgue-number-four-face-radius-exit-nonescape}
The four-face $\FiniteLebesgueNumberUp$ radius exit package exports no open-cover compactness row, selected subcover row, host minimum row, quotient stream equality row, selected limit row, choice row, or detached $\RealUp$ completeness row. Any claimed compact, continuous, totally bounded, compact-net, or uniform-modulus use of such a row is outside the admitted open-phase root-radius exit.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberFourFaceRadiusExitNonescape}
\begin{proof}
Read the positive source from coverage and exactness. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-coverage} and \autoref{thm:finite-lebesgue-number-root-radius-export-exactness} leave only the dyadic cover, rational-ball radius, dyadic mesh, four source faces, and BEDC support rows available to an accepted root-radius exit.

Then apply the existing refusal boundary. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal} removes open-cover compactness, selected subcovers, host minima, quotient stream equality, countable choice coordinates, detached $\RealUp$ completeness, and external modulus data from the open-phase root-unblock obligation packet.

Finally close the endpoint escapes. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} exhausts downstream consumer reads by the same Phase Real and Completion packet, and \autoref{thm:finite-lebesgue-number-regseq-streamname-nonescape} blocks replacement of the $\StreamNameUp$ and $\RegSeqRatUp$ faces by quotient stream equality, selected representatives, choice, selected limits, or ambient completeness. Hence none of the listed rows can be exported from the four-face radius exit package.
\end{proof}
