\begin{theorem}[Finite Lebesgue-number open Phase source nonescape]
\label{thm:finite-lebesgue-number-open-phase-source-nonescape}
For an accepted $\FiniteLebesgueNumberUp$ carrier, no public source read visible at the root can inspect host $\RealUp$ equality, open-cover compactness, choice-selected subcovers, or external modulus data before the read has passed through the finite four-face route
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
The only admissible source coordinates before that passage are the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows tied to the dyadic cover, rational-ball radius, dyadic mesh, stream name, regular rational, and Real endpoint rows of the $\FiniteLebesgueNumberUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseSourceNonescape}
\begin{proof}
Begin with the finite carrier. \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger} lists the root radius-window rows as a finite packet over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Apply the source locks. \autoref{thm:finite-lebesgue-number-l10-source-lock} forces the radius source through the stream, regular-rational, Real, mesh, and cover rows, while \autoref{thm:finite-lebesgue-number-phase-real-source-lock} exposes the same route to compact and continuous consumers without adding an outside coordinate.

Now use root radius-window exactness. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} excludes open-cover compactness, host minima, choice coordinates, quotient equality, selected limits, and detached Real-completeness data from the root obligation surface.

Therefore any accepted public source read must pass through the four displayed Phase Real faces before a downstream consumer can inspect it. Since no host equality, open-cover compactness, choice-selected subcover, or external modulus coordinate appears in the finite packet, none can be read at the root.
\end{proof}

\begin{theorem}[Finite Lebesgue-number four-face radius readback]
\label{thm:finite-lebesgue-number-four-face-radius-readback}
Every $\CompactMetricUp$, $\TotallyBoundedUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, or $\UniformModulusUp$ radius read admitted downstream of $\FiniteLebesgueNumberUp$ factors through the four L10 faces
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp
$$
together with the $\DyadicCoverUp$, $\DyadicMeshUp$, and $\RationalBallUp$ rows of the finite Lebesgue-number carrier. Thus compact and compact-net consumers can read only the displayed finite radius ledger, not an open-cover compactness principle, host minimum, arbitrary subcover, selected limit, or external modulus selector.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberFourFaceRadiusReadback}
\begin{proof}
First read the public export. \autoref{thm:finite-lebesgue-number-public-compact-uniform-export} identifies the consumer-facing export as the finite cover, rational-ball, mesh, source, transport, replay, provenance, and naming route.

Next apply the Phase Real coverage export. \autoref{thm:finite-lebesgue-number-real-phase-coverage-export} routes compact, compact-net, continuous-map, and uniform-modulus endpoints through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the finite carrier rows.

Use the root radius-window consumer exactness theorem for the compact side. \autoref{thm:finite-lebesgue-number-root-radius-window-consumer-exactness} says that the downstream consumers receive exactly the displayed finite rows and no open-cover compactness, host minimum, choice, quotient equality, selected limit, or Real-completeness coordinate.

The remaining rows $\DyadicCoverUp$, $\DyadicMeshUp$, and $\RationalBallUp$ are precisely the cover, mesh, and radius rows named in the carrier. Hence every radius read factors through the four L10 faces plus those finite dyadic rows, with no separate compactness or selector interface.
\end{proof}

\begin{theorem}[Finite Lebesgue-number root-unblock exit triad]
\label{thm:finite-lebesgue-number-root-unblock-exit-triad}
\autoref{thm:finite-lebesgue-number-open-phase-source-nonescape}, \autoref{thm:finite-lebesgue-number-four-face-radius-readback}, and \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} form the root-unblock exit surface for every compact-uniform consumer of $\FiniteLebesgueNumberUp$. The exit surface supplies only the finite four-face Phase Real route, the dyadic cover, dyadic mesh, rational-ball radius, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it supplies no host Real equality, open-cover compactness, choice-selected subcover, selected limit, detached completeness primitive, or external modulus data.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootUnblockExitTriad}
\begin{proof}
Start with the source boundary. \autoref{thm:finite-lebesgue-number-open-phase-source-nonescape} prevents a root read from reaching host Real equality, open-cover compactness, selected subcovers, or external modulus data before it passes through the four-face Phase Real route.

Now read the radius boundary. \autoref{thm:finite-lebesgue-number-four-face-radius-readback} sends every compact or compact-net radius read through the four L10 faces and the displayed dyadic cover, dyadic mesh, and rational-ball rows.

Finally apply the existing consumer boundary. \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} excludes open-cover compactness, host minima, selected subcovers, quotient equality, choice, and external modulus data from the compact, compact-net, and uniform consumer endpoints.

Combining the three rows gives exactly the root-unblock exit surface. All exported data is already present in the finite carrier and its NameCert rows, so downstream compact-uniform consumers cannot recover any outside compactness, equality, choice, completeness, selected-limit, or modulus primitive from the handoff.
\end{proof}
