\begin{theorem}[Finite Lebesgue-number open Phase radius classifier pullback]
\label{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback}
For an accepted $\FiniteLebesgueNumberUp$ positive-radius read visible at the open Phase boundary, the radius classifier factors through exactly the $\DyadicCoverUp$ row, the $\RationalBallUp$ radius row, the $\DyadicMeshUp$ row, and the four-face source route
$$
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp .
$$
The only structural support available to the read is the displayed $\BHist$ packet together with componentwise $\hsame$, displayed $\Cont$, $\Pkg$ provenance, and local $\NameCert$ naming. In particular the pullback has no coordinate for open-cover compactness, a selected subcover, a host minimum, quotient equality, choice, an external modulus, or a detached Real-completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseRadiusClassifierPullback}
\begin{proof}
Start with the Phase Real source lock. \autoref{thm:finite-lebesgue-number-phase-real-source-lock} sends every compact- or continuous-visible radius read through the dyadic cover, rational-ball radius, dyadic mesh, stream-name, regular-rational, and Real rows, while preserving only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Next use the four-face readback. \autoref{thm:finite-lebesgue-number-four-face-radius-readback} identifies the same radius read with the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route. Thus the classifier cannot acquire a second source after it crosses the open Phase boundary.

Finally apply the root consumer boundary and the nonescape triad. \autoref{thm:finite-lebesgue-number-root-radius-window-consumer-exactness} fixes the downstream rows available to compact, compact-net, continuous-map, and uniform-modulus consumers, and \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} removes open-cover compactness, selected subcovers, host minima, quotient equality, choice, and external modulus data from those endpoints. The stated pullback is therefore exactly the displayed finite classifier route.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact-uniform four-face readiness]
\label{thm:finite-lebesgue-number-compact-uniform-four-face-readiness}
Every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, and $\UniformModulusUp$ consumer downstream of the accepted $\FiniteLebesgueNumberUp$ radius ledger reads the same four-face packet
$$
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp
$$
together with the $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The compact-uniform handoff supplies no open-cover compactness, selected subcover, host minimum, quotient equality, choice, external modulus, or Real-completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactUniformFourFaceReadiness}
\begin{proof}
First read the radius classifier through the open Phase pullback. \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} gives the exact four-face source route and the dyadic cover, rational-ball, and dyadic-mesh rows available to any accepted positive-radius read.

Now attach the compact and uniform consumers. \autoref{thm:finite-lebesgue-number-root-radius-window-consumer-exactness} states that $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ consumers receive exactly the root finite rows and no outside compactness, equality, selected-limit, choice, or completeness coordinate.

Finally use the nonescape boundary. \autoref{thm:finite-lebesgue-number-consumer-nonescape-triad} excludes open-cover compactness, selected subcovers, host minima, quotient equality, choice, and external modulus data from the compact, compact-net, and uniform endpoints. Therefore the compact-uniform route is ready precisely over the four-face packet and not over an additional compactness or completeness principle.
\end{proof}

\begin{theorem}[Finite Lebesgue-number root-unblock terminal package]
\label{thm:finite-lebesgue-number-root-unblock-terminal-package}
The accepted $\FiniteLebesgueNumberUp$ root radius ledger is terminal for the current four-face route: the open Phase radius classifier pullback of \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback}, the compact-uniform readiness of \autoref{thm:finite-lebesgue-number-compact-uniform-four-face-readiness}, the Real-completion terminal-radius exhaustion of \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion}, and the L10 phase consumer readiness of \autoref{thm:finite-lebesgue-number-l10-phase-consumer-readiness} form one certificate over
$$
\DyadicCoverUp,\RationalBallUp,\DyadicMeshUp,\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
No downstream $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, or $\UniformModulusUp$ consumer in this terminal certificate can import open-cover compactness, a selected subcover, a host minimum, quotient equality, choice, an external modulus, a selected limit, or a detached Real-completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootUnblockTerminalPackage}
\begin{proof}
Begin with the two classifier surfaces. \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} fixes the accepted radius read to the dyadic cover, rational-ball, dyadic-mesh, and four-face source rows, and \autoref{thm:finite-lebesgue-number-compact-uniform-four-face-readiness} makes the compact, compact-net, and uniform consumers read that same packet.

Next attach the terminal Real-completion route. \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion} says that every compact, compact-net, continuous-map, or uniform-modulus positive-radius read factors through the terminal L10 packet and has no coordinate for open-cover compactness, host minima, quotient equality, selected limits, choice, or Real completeness.

Finally use L10 phase consumer readiness. \autoref{thm:finite-lebesgue-number-l10-phase-consumer-readiness} places the compact, compact-net, continuous-map, and uniform-modulus endpoints on the same finite route, so the classifier and terminal-radius rows are not separate certificates. The combined root ledger is therefore the stated terminal certificate, with all listed outside compactness, equality, choice, modulus, selected-limit, and completeness data excluded.
\end{proof}
