\begin{definition}[Finite Lebesgue-number Phase Real radius-window carrier]
\label{def:finite-lebesgue-number-phase-real-radius-window-carrier}
For an accepted $\FiniteLebesgueNumberUp$ route, the Phase Real radius-window carrier is the finite $\BHist$ packet
$$
\mathcal{W}_{\lambda}^{\mathrm{PhaseReal}}=(E,R,D,W,S,H,C,P,N)
$$
where $E$ is the finite Lebesgue-number request row, $R$ is the rational-ball radius row, $D$ is the $\DyadicRatCoreUp$ radius readback row, $W$ is the finite $\StreamNameUp$ window row, $S$ is the $\RegSeqRatUp$-to-$\RealUp$ seal route, and $H,C,P,N$ are the componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and compatible local $\NameCert$ rows. The carrier is read against the four source chapters \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}; it contains no quotient-stream coordinate, host-limit coordinate, countable-choice coordinate, open-cover compactness coordinate, or ambient Real-completeness coordinate.
\end{definition}

\begin{theorem}[Finite Lebesgue-number dyadic radius-window admission]
\label{thm:finite-lebesgue-number-dyadic-radius-window-admission}
Every admitted radius-window read of an accepted $\FiniteLebesgueNumberUp$ Phase Real carrier exposes the $\DyadicRatCoreUp$ radius readback row $D$ before the finite $\StreamNameUp$ window row $W$. Equivalently, a downstream compact, continuous, totally bounded, or uniform consumer may read $W$ only as part of the packet $\mathcal{W}_{\lambda}^{\mathrm{PhaseReal}}$ of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}, with the displayed dyadic radius read already present.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusWindowAdmission}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberDyadicRadiusWindowAdmission}
\begin{proof}
Start with the carrier definition. The packet $\mathcal{W}_{\lambda}^{\mathrm{PhaseReal}}$ places the finite Lebesgue-number request $E$, the rational-ball radius row $R$, and the $\DyadicRatCoreUp$ readback row $D$ before the finite stream window $W$ is available to any consumer.

The existing root and open Phase surfaces give the same order at the chapter boundary. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} identifies the positive radius and finite-window obligations with the dyadic, stream, regular-rational, Real, history, transport, continuation, provenance, and naming rows. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} then exports the root radius read through the finite dyadic and four-face Real packet.

Finally use the Phase Real audit and source exactness. \autoref{thm:finite-lebesgue-number-phase-real-radius-audit-carrier} and \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} keep the consumer-visible radius inside $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support. Since $W$ has no row outside this packet, an admitted window read can occur only after $D$ has been displayed.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Real seal radius readback]
\label{thm:finite-lebesgue-number-real-seal-radius-readback}
Any $\RealUp$ seal read used by an accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window carrier factors through the ordered rows
$$
D,\quad W,\quad S
$$
of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}. Thus the Real-side radius is read back only through the $\DyadicRatCoreUp$ radius row, the finite $\StreamNameUp$ window row, and the $\RegSeqRatUp$-to-$\RealUp$ seal route, together with the shared $H,C,P,N$ support.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRealSealRadiusReadback}
\begin{proof}
First expose the dyadic admission. By \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission}, an admitted radius-window read displays $D$ before $W$. The dyadic readback is therefore already part of the carrier before the stream window is inspected.

Next attach the regular-rational and Real faces. \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} routes every consumer-visible radius through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$. The definition of $\mathcal{W}_{\lambda}^{\mathrm{PhaseReal}}$ records the $\RegSeqRatUp$-to-$\RealUp$ part of this route as $S$.

The terminal boundary supplies the readback exclusion. \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion} keeps terminal radius reads on the same L10 packet and denies host minima, quotient equality, selected limits, countable choice, and detached Real completeness at the Real boundary. Hence any Real seal read factors through $D,W,S$ and the common $H,C,P,N$ rows, rather than through an off-packet Real source.
\end{proof}

\begin{theorem}[Finite Lebesgue-number open Phase radius-window nonescape]
\label{thm:finite-lebesgue-number-open-phase-nonescape}
No accepted $\FiniteLebesgueNumberUp$ open Phase radius-window carrier can escape to quotient streams, host limits, countable choice, open-cover compactness, or ambient Real completeness. Every admitted compact, continuous, totally bounded, compact-net, or uniform radius read remains inside the finite packet
$$
E,\quad R,\quad D,\quad W,\quad S,\quad H,\quad C,\quad P,\quad N
$$
of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}.
\end{theorem}
\begin{proof}
Begin with the two positive readback gates. \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission} forces the window side to expose the $\DyadicRatCoreUp$ row before $\StreamNameUp$ can be consumed. \autoref{thm:finite-lebesgue-number-real-seal-radius-readback} then factors each Real seal read through $D,W,S$ with the shared support rows.

Now read the existing nonescape boundaries. \autoref{thm:finite-lebesgue-number-open-phase-source-nonescape} keeps the open Phase source from bypassing the stream and regular-rational rows through host sequences, quotient stream equality, selected representatives, choice, or ambient completeness. \autoref{thm:finite-lebesgue-number-regseq-streamname-nonescape} gives the same refusal for the $\StreamNameUp$ and $\RegSeqRatUp$ faces.

Finally apply terminal and consumer exhaustion. \autoref{thm:finite-lebesgue-number-terminal-radius-phase-consumer-nonescape} and \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} keep compact, compact-net, continuous, totally bounded, and uniform consumers inside the four-face Phase Real and Completion packet. Since the carrier itself has no coordinate for quotient streams, host limits, countable choice, open-cover compactness, or ambient Real completeness, none of those rows can be exported from an admitted radius-window read.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberOpenPhaseNonescape}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-window no extra source]
\label{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source}
Every accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window packet may read only the rows
$$
D,\quad W,\quad S,\quad H,\quad C,\quad P,\quad N
$$
of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}, together with the displayed finite history $\BHist$ and its componentwise $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support. In particular, the packet has no readable source beyond the $\DyadicRatCoreUp$ endpoint and radius row, the $\StreamNameUp$ finite-window row, the $\RegSeqRatUp$ regularity and classifier row, and the $\RealUp$ seal row.
\end{theorem}
\begin{proof}
Read the packet from its carrier definition. The only source chapters named there are \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}; the remaining coordinates are the displayed finite history, transport, continuation, provenance, and local naming rows.

The three local gates make these coordinates exhaustive. \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission} exposes $D$ before $W$, \autoref{thm:finite-lebesgue-number-real-seal-radius-readback} factors the Real-side read through $D,W,S$, and \autoref{thm:finite-lebesgue-number-open-phase-nonescape} denies quotient streams, host limits, countable choice, open-cover compactness, and ambient Real completeness.

Thus any admitted consumer read is already a read of the four named faces plus the displayed BEDC support rows. Since the carrier contains no further coordinate and the nonescape theorem denies the standard off-packet exits, there is no extra source available to the radius-window packet.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusWindowNoExtraSource}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-window face minimality]
\label{thm:finite-lebesgue-number-phase-real-radius-window-face-minimality}
The four source faces of an accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window packet are minimal for the exit route. Removing the $\DyadicRatCoreUp$ face loses the endpoint and radius row $D$; removing the $\StreamNameUp$ face loses the finite-window row $W$; removing the $\RegSeqRatUp$ face loses the regularity and classifier row in $S$; and removing the $\RealUp$ face loses the terminal seal row read through $S$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusWindowFaceMinimality}
\begin{proof}
For the dyadic face, use \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission}. The theorem makes the $\DyadicRatCoreUp$ row a prerequisite for consuming the finite window, so deleting that face removes the endpoint and radius read needed before $W$ can be inspected.

For the stream face, the same admission theorem identifies $W$ as the finite window available to downstream compact, continuous, totally bounded, and uniform consumers. Without $\StreamNameUp$, the packet still has a dyadic radius row, but it has no finite-window row to present at the consumer boundary.

For the regular-rational and Real faces, use \autoref{thm:finite-lebesgue-number-real-seal-radius-readback}. The readback factors Real-side radius access through $D,W,S$, where $S$ records the $\RegSeqRatUp$-to-$\RealUp$ seal route. Removing $\RegSeqRatUp$ deletes the regularity and classifier part of $S$, while removing $\RealUp$ deletes the terminal seal part of the same row.

\autoref{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source} supplies the converse exclusion needed for minimality: none of these losses can be repaired by an off-packet source. Hence each of the four faces is necessary for the corresponding radius-window row.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-window exit consumer readiness]
\label{thm:finite-lebesgue-number-phase-real-radius-window-exit-consumer-readiness}
The accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window packet is ready for downstream compact, continuous, totally bounded, compact-net, and uniform consumers. Such a consumer may use the dyadic admission row, the Real seal readback row, the open Phase nonescape boundary, the no-extra-source boundary, and the four-face minimality boundary as one finite radius ledger, without quotient streams, selected limits, host real equality, ambient Real completeness, metric-completeness, or countable choice.
\end{theorem}
\begin{proof}
Assemble the positive ledger first. \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission} provides the ordered dyadic-to-window read, and \autoref{thm:finite-lebesgue-number-real-seal-radius-readback} routes the Real seal through $D,W,S$ with the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next attach the boundary conditions. \autoref{thm:finite-lebesgue-number-open-phase-nonescape} keeps every admitted consumer read inside the finite packet, while \autoref{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source} states that no fifth source face is readable from that packet.

Finally use \autoref{thm:finite-lebesgue-number-phase-real-radius-window-face-minimality} to make the ledger exit-ready rather than merely admissible. Each of the four source faces is required for its corresponding endpoint, finite-window, regularity, classifier, or seal row, and the nonescape boundary prevents replacement by quotient streams, selected limits, host real equality, ambient Real completeness, metric-completeness, or countable choice. This is exactly the finite radius ledger needed by downstream Phase Real consumers.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusWindowExitConsumerReadiness}

\begin{theorem}[Finite Lebesgue-number Phase Real local radius determinacy]
\label{thm:finite-lebesgue-number-phase-real-local-radius-determinacy}
Let two admitted downstream reads of an accepted $\FiniteLebesgueNumberUp$ Phase Real exit consumer use the same rows
$$
E,\quad R,\quad D,\quad W,\quad S,\quad H,\quad C,\quad P,\quad N
$$
from \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}. Then the two reads expose the same local radius-window packet $\mathcal{W}_{\lambda}^{\mathrm{PhaseReal}}$. In particular, the consumer-visible dyadic radius, finite stream window, regular-rational seal route, Real seal row, history transport, continuation replay, provenance row, and local $\NameCert$ row are fixed by the displayed packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealLocalRadiusDeterminacy}
\begin{proof}
Start from the carrier definition. The Phase Real radius-window packet is exactly the finite $\BHist$ tuple $(E,R,D,W,S,H,C,P,N)$, so equality of the displayed rows identifies the packet before any consumer interpretation is applied.

The positive readback gates make the identification local at the two consumer reads. By \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission}, both reads must expose the same dyadic radius row $D$ before the same finite window row $W$. By \autoref{thm:finite-lebesgue-number-real-seal-radius-readback}, the Real-side radius access in both reads factors through the same ordered $D,W,S$ rows with the same support.

It remains to rule out a hidden source of disagreement. \autoref{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source} denies any readable source beyond the four named faces and the support rows, while \autoref{thm:finite-lebesgue-number-phase-real-radius-window-face-minimality} makes those four faces necessary for the exit route. Hence two accepted reads with the same packet rows cannot expose distinct local radius-window data.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-window source lock]
\label{thm:finite-lebesgue-number-phase-real-radius-window-source-lock}
Every accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window exit read has its source locked to the four faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
The rows $D,W,S,H,C,P,N$ of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier} may be consumed only through these faces and their displayed finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusWindowSourceLock}
\begin{proof}
The carrier definition names exactly the four source chapters $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ for the radius-window packet. The remaining entries are not new sources; they are the finite history, transport, continuation, provenance, and naming rows used to read those faces.

The admission and readback results fix the order of access. \autoref{thm:finite-lebesgue-number-dyadic-radius-window-admission} locks the finite window behind the dyadic radius row, and \autoref{thm:finite-lebesgue-number-real-seal-radius-readback} locks the Real-side seal behind the ordered $D,W,S$ route.

Finally, \autoref{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source} excludes a fifth readable source, and \autoref{thm:finite-lebesgue-number-phase-real-radius-window-face-minimality} shows that none of the four faces can be removed from the exit route. The accepted read is therefore source-locked to precisely the displayed four-face packet.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius consumer nonescape]
\label{thm:finite-lebesgue-number-phase-real-radius-consumer-nonescape}
Compact, continuous, totally bounded, compact-net, and uniform consumers of an accepted $\FiniteLebesgueNumberUp$ Phase Real radius-window exit read cannot create an additional radius source. Any radius data they expose is already read from the packet
$$
E,\quad R,\quad D,\quad W,\quad S,\quad H,\quad C,\quad P,\quad N
$$
of \autoref{def:finite-lebesgue-number-phase-real-radius-window-carrier}, with source locked to $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusConsumerNonescape}
\begin{proof}
Use the consumer-readiness theorem as the entry point. \autoref{thm:finite-lebesgue-number-phase-real-radius-window-exit-consumer-readiness} packages the dyadic admission row, the Real seal readback row, the open Phase nonescape boundary, the no-extra-source boundary, and the four-face minimality boundary as one finite radius ledger for these consumers.

The local determinacy theorem then fixes repeated reads of that ledger. By \autoref{thm:finite-lebesgue-number-phase-real-local-radius-determinacy}, two accepted consumer reads with the same rows expose the same local radius-window packet. By \autoref{thm:finite-lebesgue-number-phase-real-radius-window-source-lock}, that packet is locked to the four named source faces and their support rows.

Thus a compact, continuous, totally bounded, compact-net, or uniform consumer has no constructor site for an additional radius source. Any consumer-visible radius row is already one of the displayed packet rows, and the exclusions in \autoref{thm:finite-lebesgue-number-phase-real-radius-window-no-extra-source} prevent quotient streams, selected limits, host real equality, ambient Real completeness, metric-completeness, or countable choice from supplying another source.
\end{proof}
