\begin{definition}[Finite Lebesgue-number Phase Real radius audit packet]
\label{def:finite-lebesgue-number-phase-real-radius-audit-packet}
For an accepted $\FiniteLebesgueNumberUp$ route, the Phase Real radius audit packet is the finite $\BHist$ row
$$
\mathcal{A}_{\lambda}^{\mathrm{PhaseReal}}=(D,\rho,M,K,S,Q,R,H,C,P,N)
$$
whose entries are the displayed positive radius ledger $\rho$, the $\DyadicCoverUp$ cover row $D$, the $\RationalBallUp$ radius row carried by $\rho$, the $\DyadicMeshUp$ mesh row $M$, the $\DyadicRatCoreUp$ core row $K$, the $\StreamNameUp$ stream row $S$, the $\RegSeqRatUp$ regular-rational row $Q$, the $\RealUp$ endpoint row $R$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ naming $N$. The packet audits only these rows and contains no open-cover compactness, selected subcover, quotient equality, choice, external modulus, selected limit, or detached Real-completeness coordinate.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusAuditPacket}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusAuditPacket\_certificate}

\begin{theorem}[Finite Lebesgue-number Phase Real radius audit carrier]
\label{thm:finite-lebesgue-number-phase-real-radius-audit-carrier}
Every accepted $\FiniteLebesgueNumberUp$ root radius read visible to the current Real and Completion route carries a unique audit packet of \autoref{def:finite-lebesgue-number-phase-real-radius-audit-packet}. The carrier consists exactly of the positive radius ledger together with
$$
\DyadicCoverUp,\RationalBallUp,\DyadicMeshUp,\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
No additional compactness, choice, quotient-equality, external-modulus, selected-limit, or Real-completeness row is part of the carrier.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusAuditCarrier}
\begin{proof}
Begin with the root radius-window obligation surface. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} displays the positive radius and finite-window obligations as finite dyadic cover, rational-ball, mesh, stream-name, regular-rational, Real, history, transport, continuation, provenance, and naming rows.

Next apply the open Phase radius classifier pullback. \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} identifies the same radius read with the $\DyadicCoverUp$, $\RationalBallUp$, and $\DyadicMeshUp$ rows and with the four-face route through \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

The displayed rows are precisely the entries of $\mathcal{A}_{\lambda}^{\mathrm{PhaseReal}}$. Since the cited root and pullback theorems leave no row for open-cover compactness, subcover selection, quotient equality, choice, external modulus data, selected limits, or detached Real completeness, the carrier is exactly the stated audit packet.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius audit classifier]
\label{thm:finite-lebesgue-number-phase-real-radius-audit-classifier}
The classifier of a Phase Real radius audit packet is determined by its displayed positive radius ledger and by the ordered source route
$$
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp .
$$
Thus two accepted audit packets with the same $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, four-face source route, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows expose the same radius classifier to every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusAuditClassifier}
\begin{proof}
Read the carrier theorem first. \autoref{thm:finite-lebesgue-number-phase-real-radius-audit-carrier} reduces every visible root radius read to the finite audit packet and names the four-face source route.

Now use the root radius-window consumer exactness theorem. \autoref{thm:finite-lebesgue-number-root-radius-window-consumer-exactness} states that compact, compact-net, continuous-map, and uniform-modulus endpoints receive exactly the dyadic cover, rational-ball, mesh, stream-name, regular-rational, Real, history, transport, continuation, provenance, and naming rows.

Finally apply the compact-uniform four-face readiness theorem. \autoref{thm:finite-lebesgue-number-compact-uniform-four-face-readiness} makes those endpoints read the same $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ source faces. Therefore equality of the displayed audit rows determines the downstream classifier and leaves no second classifier coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius audit nonescape]
\label{thm:finite-lebesgue-number-phase-real-radius-audit-nonescape}
No accepted Phase Real radius audit packet can be extended, without leaving the $\FiniteLebesgueNumberUp$ root-unblock route, by open-cover compactness, a selected subcover, quotient equality, choice, an external modulus, selected limits, or a detached Real-completeness row. Every downstream radius read remains inside the packet of \autoref{def:finite-lebesgue-number-phase-real-radius-audit-packet}.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusAuditNonescape}
\begin{proof}
Start with the classifier theorem above. It shows that all downstream compact, compact-net, continuous-map, and uniform-modulus reads are already determined by the displayed audit rows.

Attach the Real-completion terminal-radius exhaustion. \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion} keeps every terminal radius read on the L10 packet and excludes open-cover compactness, host minima, quotient equality, selected limits, choice, and Real completeness from the terminal route.

Then use the open Phase source nonescape and RegSeq-StreamName nonescape boundaries. \autoref{thm:finite-lebesgue-number-open-phase-source-nonescape} and \autoref{thm:finite-lebesgue-number-regseq-streamname-nonescape} prevent bypassing the $\StreamNameUp$ and $\RegSeqRatUp$ source rows through host sequences, quotient stream equality, selected representatives, choice, or ambient completeness.

Any proposed extension by one of the excluded rows would therefore have to pass through a coordinate absent from the carrier, the classifier, and the terminal Real-completion route. The extension leaves the accepted root-unblock packet, so the audit surface is nonescaping.
\end{proof}
