\begin{definition}[Finite Lebesgue-number Phase Real audit ledger]
\label{def:finite-lebesgue-number-phase-real-audit-ledger}
For an accepted $\FiniteLebesgueNumberUp$ root route, the Phase Real audit ledger is the finite $\BHist$ packet
$$
\mathcal{L}_{\lambda}^{\mathrm{audit}}=(D,B,M,E,S,Q,R,K,T,F,U,H,C,P,N)
$$
whose entries are the $\DyadicCoverUp$ cover row $D$, the $\RationalBallUp$ positive-radius row $B$, the $\DyadicMeshUp$ mesh row $M$, the $\DyadicRatCoreUp$ core-radius row $E$, the $\StreamNameUp$ finite-window row $S$, the $\RegSeqRatUp$ regular-rational row $Q$, the $\RealUp$ seal row $R$, the $\CompactMetricUp$ compact consumer row $K$, the $\TotallyBoundedUp$ compact-net admission row $T$, the $\ContinuousMapUp$ endpoint row $F$, the $\UniformModulusUp$ endpoint row $U$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and compatible local $\NameCert$ naming $N$. The ledger is accepted only when these rows read one positive radius through the same NameCert route over the four open Phase source faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealAuditLedger}

\begin{theorem}[Finite Lebesgue-number Phase Real audit-ledger source]
\label{thm:finite-lebesgue-number-phase-real-audit-ledger-source}
Every accepted Phase Real audit-ledger read for $\FiniteLebesgueNumberUp$ factors its radius source through the four open Phase faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp .
$$
The dyadic-cover, rational-ball, and dyadic-mesh rows of \autoref{def:finite-lebesgue-number-phase-real-audit-ledger} are source rows for this route, while the compact, totally bounded, continuous-map, and uniform-modulus rows are consumers of the same finite packet.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealAuditLedgerSource}
\begin{proof}
Begin with the root radius-window obligation surface. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} confines the visible positive-radius and finite-window obligations to the dyadic cover, rational-ball, mesh, stream-name, regular-rational, Real, history, transport, replay, provenance, and naming rows.

Now attach the open Phase root-unblock route. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} exposes the same root radius through the four source faces, and \autoref{thm:finite-lebesgue-number-root-radius-export-exactness} says that an admissible root-radius export is exactly the finite packet over those faces and the support rows.

Finally use the exit and window certificates. \autoref{thm:finite-lebesgue-number-four-face-radius-readback}, \autoref{thm:finite-lebesgue-number-four-face-radius-exit-coverage}, \autoref{thm:finite-lebesgue-number-four-face-radius-exit-determinacy}, and \autoref{thm:finite-lebesgue-number-four-face-radius-exit-nonescape} make the four-face route covering, deterministic, and nonescaping. The Phase Real radius-window face minimality theorem then identifies these faces as the necessary source faces for the accepted audit ledger, so every accepted read factors through them.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real audit-ledger scope]
\label{thm:finite-lebesgue-number-phase-real-audit-ledger-scope}
The scoped support of an accepted Phase Real audit ledger for $\FiniteLebesgueNumberUp$ is exactly the displayed rows
$$
\DyadicCoverUp,\RationalBallUp,\DyadicMeshUp,\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp,\CompactMetricUp,\TotallyBoundedUp,\ContinuousMapUp,\UniformModulusUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
It has no coordinate for open-cover compactness, selected subcovers, quotient streams, host minima, selected limits, countable choice, detached $\RealUp$ completeness, external modulus data, or an unbudgeted radius selector.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealAuditLedgerScope}
\begin{proof}
Read the ledger definition first. The only support rows named by $\mathcal{L}_{\lambda}^{\mathrm{audit}}$ are the dyadic cover, rational ball, mesh, four Phase Real source faces, compact and uniform consumer endpoints, finite history, transport, replay, provenance, and local naming rows.

The existing audit and window packets make this support exhaustive. \autoref{thm:finite-lebesgue-number-phase-real-radius-audit-carrier} identifies the current Real and Completion route with the dyadic cover, rational-ball, mesh, four-face, history, transport, replay, provenance, and naming rows. \autoref{thm:finite-lebesgue-number-phase-real-radius-window-face-minimality} says that none of the four faces can be removed while preserving its corresponding radius-window row.

The nonescape boundaries remove the off-table rows. \autoref{thm:finite-lebesgue-number-phase-real-radius-audit-nonescape} excludes open-cover compactness, selected subcovers, quotient equality, choice, external modulus data, selected limits, and detached Real completeness from the audit packet. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} keeps downstream consumers inside the same Phase Real and Completion packet, so host minima, quotient streams, selected limits, and unbudgeted radius selection have no scope row in the accepted ledger.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real audit-ledger readiness]
\label{thm:finite-lebesgue-number-phase-real-audit-ledger-readiness}
The Phase Real audit ledger of \autoref{def:finite-lebesgue-number-phase-real-audit-ledger} is ready for $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, compact-net, and $\UniformModulusUp$ consumers. Each of these consumers reads the same finite ledger through the root radius-window obligation surface, the open Phase root-unblock coverage, the root-radius export, the L10 consumer exhaustion, the four-face exit package, and the Phase Real radius-window face minimality boundary; none receives a private radius source.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealAuditLedgerReadiness}
\begin{proof}
Assemble the source side first. \autoref{thm:finite-lebesgue-number-phase-real-audit-ledger-source} routes every accepted audit-ledger read through the four open Phase faces, and \autoref{thm:finite-lebesgue-number-phase-real-audit-ledger-scope} fixes the support rows available to the route.

Now attach the downstream endpoints. \autoref{thm:finite-lebesgue-number-compact-uniform-four-face-readiness} places compact, compact-net, and uniform consumers on the same four-face packet. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} extends the same exhaustion to compact, continuous, totally bounded, compact-net, and uniform radius reads along the Phase Real and Completion route.

The readiness claim follows from the absence of a second source coordinate. The root radius-window obligation surface, the open Phase root-unblock radius coverage, the root-radius export exactness, the four-face exit coverage, determinacy, and nonescape theorems, and the Phase Real radius-window face minimality theorem leave the consumers with precisely the rows of $\mathcal{L}_{\lambda}^{\mathrm{audit}}$. Since the scoped ledger excludes open-cover compactness, selected subcovers, quotient streams, host minima, selected limits, countable choice, detached Real completeness, external modulus data, and unbudgeted radius selection, no consumer can read a private radius source.
\end{proof}
