\begin{definition}[Finite Lebesgue-number Phase Real radius-consumer ledger]
\label{def:finite-lebesgue-number-phase-real-radius-consumer-ledger}
For an accepted $\FiniteLebesgueNumberUp$ root route, the Phase Real radius-consumer ledger is the finite $\BHist$ packet
$$
\Lambda_{\lambda}^{\mathrm{cons}}=(D,B,M,E,S,Q,R,K,F,U,H,C,P,N).
$$
Here $D$ is the $\DyadicCoverUp$ cover row, $B$ is the $\RationalBallUp$ positive-radius row, $M$ is the $\DyadicMeshUp$ mesh row, and $E$ is the $\DyadicRatCoreUp$ face through which the radius is read before the stream face. The rows $S,Q,R$ are the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ source faces. The rows $K,F,U$ are the $\CompactMetricUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ consumer endpoints, while $H,C,P,N$ record componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and compatible local $\NameCert$ rows.

The packet is accepted only when these rows form one finite NameCert route for the same positive radius $\lambda$. A compact, continuous, or uniform endpoint may inspect $\lambda$ only through $\Lambda_{\lambda}^{\mathrm{cons}}$ and may not replace it by open-cover compactness, a host minimum, a selected subcover, quotient stream equality, a selected limit, countable choice, metric-completeness data, or a detached $\RealUp$ completeness claim.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusConsumerLedger}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-consumer carrier]
\label{thm:finite-lebesgue-number-phase-real-radius-consumer-carrier}
Every admitted $\CompactMetricUp$, $\ContinuousMapUp$, or $\UniformModulusUp$ consumer radius source downstream of an accepted $\FiniteLebesgueNumberUp$ root route projects to exactly the rows of $\Lambda_{\lambda}^{\mathrm{cons}}$ in \autoref{def:finite-lebesgue-number-phase-real-radius-consumer-ledger}. Thus the consumer-visible source is carried by
$$
\DyadicCoverUp,\quad \RationalBallUp,\quad \DyadicMeshUp,\quad \DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp,
$$
together with the endpoint rows $\CompactMetricUp,\ContinuousMapUp,\UniformModulusUp$ and the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows, and by no further radius-source coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusConsumerCarrier}
\begin{proof}
Start from the root route. \autoref{thm:finite-lebesgue-number-root-radius-choice-free-tail-exhaustion} and \autoref{thm:finite-lebesgue-number-root-radius-source-determinacy} place every compact, continuous, totally bounded, or uniform root-radius read on the shared tail-and-Real packet over the dyadic cover, rational ball, dyadic mesh, stream-name, regular-rational, Real, history, transport, replay, provenance, and naming rows.

Next attach the Real-phase source boundary. \autoref{thm:finite-lebesgue-number-real-phase-source-exhaustion} forces admitted compact, continuous, compact-net, totally bounded, and uniform radius reads through the finite Real-phase ledger, while \autoref{thm:finite-lebesgue-number-real-phase-offtable-refusal} denies substitute source coordinates outside that ledger.

Finally identify the four faces and the consumer endpoints. \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} adds the $\DyadicRatCoreUp$ face to the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route, and \autoref{thm:finite-lebesgue-number-compact-radius-window-pullback} ties the compact, continuous, and uniform endpoints to the same radius-window packet. These cited surfaces list exactly the rows of $\Lambda_{\lambda}^{\mathrm{cons}}$, so every admitted consumer source projects to that packet and to no outside radius coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-consumer stability]
\label{thm:finite-lebesgue-number-phase-real-radius-consumer-stability}
Let two accepted $\FiniteLebesgueNumberUp$ root routes carry Phase Real radius-consumer ledgers for visible radii $\lambda$ and $\mu$. If their $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$ rows agree componentwise under the recorded $\hsame$ transports, then the compact, continuous, and uniform endpoints receive the same radius-consumer source from the two routes.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusConsumerStability}
\begin{proof}
First compare the root radius sources. \autoref{thm:finite-lebesgue-number-root-radius-source-determinacy} says that componentwise agreement on the dyadic, stream, regular-rational, Real, history, replay, provenance, and naming rows fixes the downstream root-radius source for compact, continuous, totally bounded, and uniform consumers.

Now compare the compact radius-window packets. \autoref{thm:finite-lebesgue-number-compact-radius-window-pullback} and \autoref{thm:finite-lebesgue-number-uniform-modulus-consumer-pullback} make the $\CompactMetricUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ rows consume one shared finite packet, so the agreed endpoint rows cannot introduce a second source after transport.

Finally use four-face exactness. \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} fixes the consumer-visible source to the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces with the same BEDC support rows. Since each of those rows is identified by the recorded $\hsame$ transports, the compact, continuous, and uniform endpoints receive the same radius-consumer source.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Phase Real radius-consumer exhaustion]
\label{thm:finite-lebesgue-number-phase-real-radius-consumer-exhaustion}
The Phase Real radius-consumer ledger $\Lambda_{\lambda}^{\mathrm{cons}}$ exports no open-cover compactness, host minimum, selected subcover, quotient stream equality, selected limit, countable choice, metric-completeness datum, or $\RealUp$ completeness claim. Every compact, continuous, or uniform radius read admitted by the ledger is exhausted by its displayed dyadic, four-face Real, endpoint, history, transport, replay, provenance, and naming rows.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRadiusConsumerExhaustion}
\begin{proof}
Read the ledger definition first. \autoref{def:finite-lebesgue-number-phase-real-radius-consumer-ledger} lists only the dyadic cover, rational-ball radius, dyadic mesh, $\DyadicRatCoreUp$, stream-name, regular-rational, Real, compact, continuous, uniform, history, transport, replay, provenance, and naming rows.

The root and Real-phase exhaustion theorems remove the proposed outside coordinates at the source. \autoref{thm:finite-lebesgue-number-root-radius-choice-free-tail-exhaustion} excludes open-cover compactness, selected subcovers, quotient stream equality, countable choice, detached $\RealUp$ completeness, and external modulus data from the root route, while \autoref{thm:finite-lebesgue-number-real-phase-source-exhaustion} leaves every admitted endpoint read inside the finite Real-phase packet.

The compact-window and four-face theorems remove the remaining endpoint escapes. \autoref{thm:finite-lebesgue-number-compact-radius-window-pullback} excludes selected limits, quotient stream equality, selected subcovers, host minima, choice-like cover selection, and unbudgeted radius selection for compact and continuous consumers, and \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} excludes open-cover compactness, selected subcover, quotient equality, host minimum, countable choice, Real completeness, and external modulus coordinates from the four-face packet.

Combining these surfaces, every admitted compact, continuous, or uniform read is already accounted for by $\Lambda_{\lambda}^{\mathrm{cons}}$. None of open-cover compactness, a host minimum, a selected subcover, quotient stream equality, selected limits, countable choice, metric-completeness data, or a detached $\RealUp$ completeness claim has a ledger row through which it can be exported.
\end{proof}
