\begin{theorem}[Phase Real four-face source exactness]
\label{thm:finite-lebesgue-number-phase-real-four-face-source-exactness}
Every consumer-visible $\FiniteLebesgueNumberUp$ radius read in the accepted root route factors through the current Phase Real and Completion faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. The exact source packet exports no open-cover compactness, selected subcover, quotient equality, host minimum, countable choice, Real completeness, or external modulus coordinate.
\end{theorem}

\begin{proof}
Begin with the L10 source lock. \autoref{thm:finite-lebesgue-number-l10-source-lock} forces the radius route through the finite stream, regular-rational, Real, dyadic-mesh, and dyadic-cover rows before any consumer can inspect the positive-radius ledger.

Next apply the open Phase classifier. \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} identifies the visible positive-radius classifier with the four-face route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, carried by the same finite dyadic cover, rational-ball, and mesh packet.

Finally attach the Phase Real radius audit carrier. \autoref{thm:finite-lebesgue-number-phase-real-radius-audit-carrier} records the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows and excludes open-cover compactness, choice, quotient equality, external modulus data, selected limits, and detached Real-completeness rows. Since the accepted consumer read has no row outside these cited packets, the stated four-face source exactness follows.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealFourFaceSourceExactness}

\begin{theorem}[Terminal-radius Phase consumer nonescape]
\label{thm:finite-lebesgue-number-terminal-radius-phase-consumer-nonescape}
Every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, or $\UniformModulusUp$ consumer that reads a terminal $\FiniteLebesgueNumberUp$ radius remains inside the four-face Phase Real and Completion packet
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp,\quad \BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
Such a terminal consumer cannot escape to open-cover compactness, a selected subcover, quotient equality, a host minimum, countable choice, Real completeness, or an external modulus coordinate.
\end{theorem}

\begin{proof}
Start from terminal-radius exhaustion. \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion} makes every compact, compact-net, continuous-map, or uniform-modulus terminal read factor through the displayed L10 packet and denies open-cover compactness, host minima, quotient equality, selected limits, choice, and Real completeness at that boundary.

Then use the four-face exactness theorem above. It identifies the visible source of the same radius with $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ plus the BEDC support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

The compact-uniform source triangle, \autoref{thm:finite-lebesgue-number-compact-uniform-source-triangle}, places these source faces before the compact, continuous-map, and uniform-modulus endpoints. Any terminal escape would therefore require a coordinate absent from the terminal ledger and absent from the four-face source packet, so no such consumer can leave the stated route.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberTerminalRadiusPhaseConsumerNonescape}

\begin{theorem}[Phase Real root-unblock package]
\label{thm:finite-lebesgue-number-phase-real-root-unblock-package}
The $\FiniteLebesgueNumberUp$ root-unblock surface for downstream compact and uniform consumers is the single finite package consisting of the four Phase Real and Completion faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$ and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. This package is source-exact: every consumer-visible radius read factors through it, and it exports no open-cover compactness, selected subcover, quotient equality, host minimum, countable choice, Real completeness, or external modulus coordinate.
\end{theorem}

\begin{proof}
First combine source exactness with terminal nonescape. \autoref{thm:finite-lebesgue-number-phase-real-four-face-source-exactness} gives the exact source packet for any consumer-visible radius read, and \autoref{thm:finite-lebesgue-number-terminal-radius-phase-consumer-nonescape} keeps terminal compact, compact-net, continuous-map, and uniform-modulus consumers inside the same packet.

Next use the compact-uniform source triangle. \autoref{thm:finite-lebesgue-number-compact-uniform-source-triangle} orders the four source faces before the consumer endpoints and ties them to the visible dyadic cover, rational-ball, mesh, history, transport, continuation, provenance, and naming rows.

The open Phase radius classifier pullback and Real-completion terminal-radius exhaustion supply the two boundary checks: \autoref{thm:finite-lebesgue-number-open-phase-radius-classifier-pullback} fixes the classifier before the consumer endpoint can read it, while \autoref{thm:finite-lebesgue-number-real-completion-terminal-radius-exhaustion} rules out the off-packet compactness, equality, choice, completeness, and modulus coordinates at the terminal boundary. The root-unblock surface is therefore exactly the stated finite package.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealRootUnblockPackage}
