\section{Finite Lebesgue-number Phase Real terminal radius readiness}
\label{sec:finite-lebesgue-number-phase-real-terminal-radius-readiness}

\begin{definition}[Finite Lebesgue-number Phase Real terminal radius readiness ledger]
\label{def:finite-lebesgue-number-phase-real-terminal-radius-readiness-ledger}
For an accepted $\FiniteLebesgueNumberUp$ route, the Phase Real terminal radius readiness ledger is the finite $\BHist$ packet
$$
\mathcal{T}_{\lambda}^{\mathrm{ready}}=(D,B,M,E,S,Q,R,K,F,T,U,H,C,P,N)
$$
whose entries are the $\DyadicCoverUp$ cover row $D$, the $\RationalBallUp$ positive-radius row $B$, the $\DyadicMeshUp$ mesh row $M$, the $\DyadicRatCoreUp$ core-radius face $E$, the $\StreamNameUp$ window face $S$, the $\RegSeqRatUp$ regular-rational face $Q$, the $\RealUp$ endpoint face $R$, the $\CompactMetricUp$ compact consumer row $K$, the $\ContinuousMapUp$ continuous endpoint row $F$, the $\TotallyBoundedUp$ finite-net consumer row $T$, the $\UniformModulusUp$ uniform endpoint row $U$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and compatible local $\NameCert$ naming $N$.

The ledger is accepted only when the compact, continuous, totally bounded, compact-net, and uniform consumers read one terminal positive-radius verdict through the same dyadic and four-face Phase Real packet. In particular, the verdict is carried by the displayed $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces and by the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows; it is not a host minimum, an open-cover compactness row, a selected subcover, a quotient stream equality, a selected limit, countable choice, detached $\RealUp$ completeness, or an external modulus datum.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealTerminalRadiusReadinessLedger}

\begin{theorem}[Finite Lebesgue-number Phase Real terminal radius readiness]
\label{thm:finite-lebesgue-number-phase-real-terminal-radius-readiness}
Every accepted terminal radius consumer for $\FiniteLebesgueNumberUp$ factors through the ledger of \autoref{def:finite-lebesgue-number-phase-real-terminal-radius-readiness-ledger}. Equivalently, each $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, compact-net, or $\UniformModulusUp$ consumer visible at the Phase Real terminal boundary receives the same finite packet
$$
D,B,M,E,S,Q,R,K,F,T,U,H,C,P,N
$$
and receives no private positive-radius source outside that packet.
\end{theorem}
\begin{proof}
Start with the root-unblock surface. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-radius-coverage} puts every accepted root radius read inside the finite dyadic cover, rational-ball, dyadic-mesh, four-face Real, history, transport, replay, provenance, and naming packet, while \autoref{thm:finite-lebesgue-number-root-radius-export-exactness} identifies admissible root-radius export with displaying exactly that packet.

Next attach the terminal consumer rows. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} exhausts compact, continuous, totally bounded, and uniform radius reads by the same Phase Real and Completion packet. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-coverage} adds the compact-net consumer to the same four-face exit package, so every listed endpoint reads the displayed dyadic and Phase Real rows before any consumer verdict is available.

Finally use the audit readiness boundary. \autoref{thm:finite-lebesgue-number-phase-real-audit-ledger-readiness} states that compact, continuous, totally bounded, compact-net, and uniform consumers read the same finite ledger through the root radius-window obligation surface, open Phase root-unblock coverage, root-radius export, L10 consumer exhaustion, four-face exit package, and Phase Real radius-window face minimality boundary. These are precisely the rows of $\mathcal{T}_{\lambda}^{\mathrm{ready}}$, so every accepted terminal consumer factors through the readiness ledger and cannot add a private positive-radius source.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealTerminalRadiusReadiness}

\begin{theorem}[Finite Lebesgue-number Phase Real terminal radius stability]
\label{thm:finite-lebesgue-number-phase-real-terminal-radius-stability}
Componentwise $\hsame$ transport and displayed $\Cont$ replay preserve the terminal radius verdict of \autoref{def:finite-lebesgue-number-phase-real-terminal-radius-readiness-ledger} exactly when they preserve the displayed $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, $\UniformModulusUp$, $\BHist$, $\Pkg$, and $\NameCert$ rows componentwise. Under such transport, the compact, continuous, totally bounded, compact-net, and uniform consumers read the same terminal verdict.
\end{theorem}
\begin{proof}
First reduce the verdict to the root packet. By \autoref{thm:finite-lebesgue-number-root-radius-export-exactness}, an admissible root-radius export is exactly the finite packet over the dyadic cover, rational-ball, mesh, four source faces, and BEDC support rows. \autoref{thm:finite-lebesgue-number-open-phase-positive-radius-stability} then says that componentwise $\hsame$ transport and displayed $\Cont$ replay preserve the positive-radius row only together with its rational-ball, mesh, stream, regular-rational, and Real rows.

Next compare the consumer endpoints. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-determinacy} makes agreement on the four source faces and the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows determine the downstream radius classifier seen by compact, continuous, totally bounded, compact-net, and uniform consumers. Thus componentwise transport of the rows listed in $\mathcal{T}_{\lambda}^{\mathrm{ready}}$ transports the consumer-visible verdict as one packet.

The converse is forced by nonescape. If the terminal verdict were preserved while one displayed source or support row changed, the endpoint would require an unrecorded replacement coordinate for the missing row. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-nonescape} and \autoref{thm:finite-lebesgue-number-phase-real-audit-ledger-scope} exclude precisely those outside coordinates. Hence terminal verdict stability is exactly componentwise $\hsame$ and displayed $\Cont$ stability of the ledger rows.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealTerminalRadiusStability}

\begin{theorem}[Finite Lebesgue-number Phase Real terminal radius nonescape]
\label{thm:finite-lebesgue-number-phase-real-terminal-radius-nonescape}
The Phase Real terminal radius readiness ledger exports no open-cover compactness row, selected-subcover row, host-minimum row, quotient stream equality row, selected-limit row, countable-choice row, detached $\RealUp$ completeness row, or external-modulus row. Any compact, continuous, totally bounded, compact-net, or uniform-modulus terminal use of such a row lies outside the accepted $\FiniteLebesgueNumberUp$ terminal radius route.
\end{theorem}
\begin{proof}
Read the positive source first. \autoref{thm:finite-lebesgue-number-open-phase-root-unblock-choice-refusal} removes open-cover compactness, selected subcovers, host minima, quotient stream equality, countable choice coordinates, detached $\RealUp$ completeness, and external modulus data from the open Phase root-unblock obligation packet.

Now pass through the four-face exit package. \autoref{thm:finite-lebesgue-number-four-face-radius-exit-nonescape} excludes open-cover compactness, selected subcovers, host minima, quotient stream equality, selected limits, choice rows, and detached $\RealUp$ completeness from the four-face radius exit. \autoref{thm:finite-lebesgue-number-l10-consumer-radius-exhaustion} keeps compact, continuous, totally bounded, and uniform consumers inside the same Phase Real and Completion packet.

Finally attach the terminal ledger. \autoref{thm:finite-lebesgue-number-phase-real-audit-ledger-scope} lists exactly the dyadic, four-face Real, compact, continuous, totally bounded, uniform, history, transport, replay, provenance, and naming rows available to the audit route, and \autoref{thm:finite-lebesgue-number-phase-real-terminal-radius-readiness} makes every accepted terminal consumer factor through those rows. Since none of the excluded objects has a coordinate in $\mathcal{T}_{\lambda}^{\mathrm{ready}}$, no accepted terminal consumer can export or inspect such an object.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealTerminalRadiusNonescape}

\begin{theorem}[Finite Lebesgue-number Phase Real terminal radius choice-free finality]
\label{thm:finite-lebesgue-number-phase-real-terminal-radius-choice-free-finality}
For $\FiniteLebesgueNumberUp$, every accepted Phase Real terminal radius verdict is final exactly as the finite packet $D,B,M,E,S,Q,R,K,F,T,U,H,C,P,N$ of \autoref{def:finite-lebesgue-number-phase-real-terminal-radius-readiness-ledger}. If another accepted terminal verdict is visible at the same boundary, then it agrees componentwise on the $\DyadicCoverUp$ cover row, $\RationalBallUp$ positive-radius row, $\DyadicMeshUp$ mesh row, $\DyadicRatCoreUp$ core-radius face, $\StreamNameUp$ window face, $\RegSeqRatUp$ regular-rational face, $\RealUp$ endpoint face, $\CompactMetricUp$ compact consumer row, $\ContinuousMapUp$ continuous endpoint row, $\TotallyBoundedUp$ finite-net row, $\UniformModulusUp$ uniform endpoint row, $\BHist$ transport ledger, displayed continuation row, $\Pkg$ provenance row, and compatible $\NameCert$ row. No compact, continuous, totally bounded, compact-net, or uniform endpoint may refine that final verdict by open-cover compactness, selected subcover, host minimum, quotient stream equality, countable choice, detached $\RealUp$ completeness, or an external modulus.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberPhaseRealTerminalRadiusChoiceFreeFinality}
\begin{proof}
First force every terminal verdict through the readiness packet. By \autoref{thm:finite-lebesgue-number-phase-real-terminal-radius-readiness}, an accepted compact, continuous, totally bounded, compact-net, or uniform endpoint reads the terminal positive-radius verdict only through the displayed rows $D,B,M,E,S,Q,R,K,F,T,U,H,C,P,N$.

Now compare two accepted terminal verdicts. \autoref{thm:finite-lebesgue-number-phase-real-terminal-radius-stability} says that preservation of the terminal verdict is exactly componentwise preservation of the dyadic cover, rational ball, dyadic mesh, DyadicRatCore, StreamName, RegSeqRat, Real, compact, continuous, totally bounded, uniform, history, provenance, and NameCert rows together with the displayed transport and continuation data. Thus two accepted terminal verdicts at the same boundary agree precisely when these coordinates agree.

The remaining visible classifier is unique. \autoref{thm:finite-lebesgue-number-open-phase-root-radius-classifier-totality} supplies the total visible root-radius classifier for the open Phase boundary, so there is no second consumer-facing classifier through which the same terminal packet could be reread as a different verdict.

Finally exclude all proposed refinements outside the packet. \autoref{thm:finite-lebesgue-number-phase-real-terminal-radius-nonescape} refuses open-cover compactness, selected subcover, host minimum, quotient stream equality, countable choice, detached $\RealUp$ completeness, and external modulus rows at this terminal boundary. Hence the accepted terminal radius verdict is final in the choice-free Phase Real sense: every second accepted verdict is the same componentwise packet, and every outside endpoint refinement is unavailable to the route.
\end{proof}
