\begin{definition}[Finite Lebesgue-number Real-phase source-exhaustion ledger]
\label{def:finite-lebesgue-number-real-phase-source-exhaustion-ledger}
For an accepted $\FiniteLebesgueNumberUp$ route, the Real-phase source-exhaustion ledger is the finite row family
$$
\Xi_{\lambda}^{\mathrm{real}}=(D,B,M,A,S,Q,R,H,C,P,N).
$$
Here $D$ is the displayed $\DyadicCoverUp$ cover row, $B$ is the $\RationalBallUp$ positive-radius row, $M$ is the $\DyadicMeshUp$ mesh row, and $A$ records the finite admissibility row through which the radius is offered to compact, continuous, totally bounded, and uniform endpoints. The rows $S,Q,R$ are the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ source faces; $H$ records the permitted $\hsame$ transports, $C$ records the $\Cont$ replay, $P$ records $\Pkg$ provenance, and $N$ records the compatible local $\NameCert$ rows.

The ledger is accepted only as one finite $\BHist$ packet. A consumer may read the radius $\lambda$ only through these rows and may not replace the packet by host $\RealUp$ equality, quotient stream equality, selected limits, detached completeness, choice, an external modulus, or arbitrary open-cover compactness.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRealPhaseSourceExhaustionLedger}

\begin{theorem}[Finite Lebesgue-number Real-phase source exhaustion]
\label{thm:finite-lebesgue-number-real-phase-source-exhaustion}
Every $\CompactMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, $\CompactNetModulusSelectorUp$, or $\UniformModulusUp$ consumer admitted by an accepted $\FiniteLebesgueNumberUp$ radius read passes through the ledger $\Xi_{\lambda}^{\mathrm{real}}$ of \autoref{def:finite-lebesgue-number-real-phase-source-exhaustion-ledger} before it can inspect the radius. Thus every compact, continuous, totally bounded, compact-net, or uniform radius read is exhausted by the finite rows
$$
D,B,M,A,S,Q,R,H,C,P,N
$$
over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRealPhaseSourceExhaustion}
\leanvariant{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCarrier\_real\_phase\_source\_exhaustion}
\begin{proof}
Start with the open Phase boundary. \autoref{thm:finite-lebesgue-number-open-phase-source-nonescape} prevents the source read from reaching host $\RealUp$ equality, open-cover compactness, selected subcovers, or external modulus data before the four-face route is consumed.

Next identify the radius readback. \autoref{thm:finite-lebesgue-number-four-face-radius-readback} says that every compact, compact-net, continuous-map, totally bounded, or uniform radius read factors through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the visible dyadic cover, rational-ball, and dyadic mesh rows.

Now pass to the L10 consumer route. \autoref{thm:finite-lebesgue-number-l10-consumer-readback-exactness} makes the consumer-facing read exact at the finite packet, while \autoref{thm:finite-lebesgue-number-compact-consumer-determinacy-package} keeps compact and compact-net endpoints from introducing a second source.

Combining those four cited surfaces gives precisely $\Xi_{\lambda}^{\mathrm{real}}$. Each named row is already in the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet, so no admitted consumer radius read has a remaining source outside the displayed ledger.
\end{proof}

\begin{theorem}[Finite Lebesgue-number compact-consumer source verdict]
\label{thm:finite-lebesgue-number-compact-consumer-source-verdict}
The compact and compact-net endpoints of an accepted $\FiniteLebesgueNumberUp$ route receive only the finite dyadic radius verdict recorded by $\Xi_{\lambda}^{\mathrm{real}}$. They receive the rows $D,B,M,A,S,Q,R,H,C,P,N$ and no open-cover compactness principle, selected subcover data, host minimum, quotient stream equality, chosen limit, detached completeness primitive, choice coordinate, or external modulus selector.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberCompactConsumerSourceVerdict}
\begin{proof}
First read the compact endpoint through determinacy. \autoref{thm:finite-lebesgue-number-compact-consumer-determinacy-package} fixes the compact and compact-net consumer verdict to the finite carrier rows and their recorded transport.

Then use radius readback exactness. \autoref{thm:finite-lebesgue-number-four-face-radius-readback} and \autoref{thm:finite-lebesgue-number-l10-consumer-readback-exactness} identify the visible radius as the dyadic cover, rational-ball radius, dyadic mesh, stream-name, regular-rational, Real endpoint, transport, replay, provenance, and naming packet.

Finally exclude outside compactness sources. The open Phase nonescape theorem removes open-cover compactness, selected subcovers, and external modulus data before the source is read, and the Real-phase source exhaustion theorem above leaves no second endpoint source after the finite packet is consumed.

Therefore compact and compact-net consumers receive exactly the finite dyadic radius verdict and none of the refused compactness, selection, equality, completeness, choice, or modulus data.
\end{proof}

\begin{theorem}[Finite Lebesgue-number Real-phase offtable refusal]
\label{thm:finite-lebesgue-number-real-phase-offtable-refusal}
The Real-and-Completion handoff of an accepted $\FiniteLebesgueNumberUp$ route refuses every radius source not listed in $\Xi_{\lambda}^{\mathrm{real}}$. In particular, host $\RealUp$ equality, quotient stream equality, selected limits, detached completeness, countable choice, an external modulus, and arbitrary open-cover compactness are offtable for every compact, continuous, totally bounded, compact-net, and uniform consumer radius read.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRealPhaseOfftableRefusal}
\begin{proof}
Read the ledger definition first. \autoref{def:finite-lebesgue-number-real-phase-source-exhaustion-ledger} lists the only rows available at the Real-and-Completion handoff: dyadic cover, rational-ball radius, dyadic mesh, finite admissibility, stream-name, regular-rational, Real endpoint, transport, replay, provenance, and local naming.

The source and readback theorems close the route around those rows. \autoref{thm:finite-lebesgue-number-open-phase-source-nonescape} prevents outside compactness or selector data from entering before the four-face source, and \autoref{thm:finite-lebesgue-number-four-face-radius-readback} forces later radius reads through the same four faces.

The consumer exactness theorems close the route at the endpoint. \autoref{thm:finite-lebesgue-number-l10-consumer-readback-exactness} identifies the consumer-visible read with the finite packet, while \autoref{thm:finite-lebesgue-number-compact-consumer-determinacy-package} prevents compact endpoints from replacing it by a separate source.

Since host $\RealUp$ equality, quotient stream equality, selected limits, detached completeness, countable choice, external modulus data, and arbitrary open-cover compactness occur in none of the accepted rows, the Real-phase handoff refuses all of them for every admitted consumer.
\end{proof}
