\begin{definition}[Finite Lebesgue-number root radius-window obligation ledger]
\label{def:finite-lebesgue-number-root-radius-window-obligation-ledger}
For an accepted $\FiniteLebesgueNumberUp$ carrier, the root radius-window obligation ledger is the finite $\BHist$ row
$$
\Omega_{\lambda W}=(D,W,\lambda,M,S,Q,R,H,C,P,N)
$$
whose entries are the $\DyadicCoverUp$ cover row $D$, the finite window row $W$, the positive radius row $\lambda$, the $\DyadicMeshUp$ mesh row $M$, the $\StreamNameUp$ source row $S$, the $\RegSeqRatUp$ regular-rational row $Q$, the $\RealUp$ endpoint row $R$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ naming $N$. The ledger records the root obligation surface only through $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; it has no coordinate for open-cover compactness, a host minimum, choice, quotient equality, selected limit data, or a separate completeness primitive.
\end{definition}
\leandef{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootRadiusWindowObligationLedger}

\begin{theorem}[Finite Lebesgue-number root radius-window obligation surface]
\label{thm:finite-lebesgue-number-root-radius-window-obligation-surface}
Every accepted root radius-window obligation ledger of \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger} discharges the positive radius and finite-window obligations only through the displayed dyadic cover, rational-ball radius, dyadic mesh, stream-name, regular-rational, Real, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. In particular, the root obligation exposed to the Real-and-completion route is the finite packet
$$
D,W,\lambda,M,S,Q,R,H,C,P,N
$$
and not an open-cover compactness principle, host minimum, choice coordinate, quotient equality, selected limit, or Real-completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootRadiusWindowObligationSurface}
\begin{proof}
Begin with the carrier. \autoref{def:finite-lebesgue-number-carrier} displays the finite dyadic cover, finite window, radius, mesh, transport, continuation, provenance, and local naming rows of the $\FiniteLebesgueNumberUp$ packet.

Apply the NameCert obligations and finite-window coverage exactness. \autoref{thm:finite-lebesgue-number-namecert-obligations} keeps each public read inside the carrier rows, while \autoref{thm:finite-lebesgue-number-window-coverage-exactness} routes every accepted window through $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, the mesh row, and the named dyadic cover row.

Now apply the L10 and Phase Real source locks. \autoref{thm:finite-lebesgue-number-l10-source-lock} and \autoref{thm:finite-lebesgue-number-phase-real-source-lock} force the positive-radius read through the dyadic, stream, regular-rational, and Real rows before any consumer can inspect it.

Thus the ledger of \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger} is exactly the root radius-window surface. Since the cited rows contain no open-cover compactness, host minimum, choice, quotient equality, selected limit, or Real-completeness coordinate, none is available at the root.
\end{proof}

\begin{theorem}[Finite Lebesgue-number radius carrier source]
\label{thm:finite-lebesgue-number-radius-carrier-source}
Every accepted $\FiniteLebesgueNumberUp$ root radius-window ledger projects its carrier source exactly to the finite $\BHist$ rows
$$
D,W,\lambda,M,S,Q,R,H,C,P,N
$$
of \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger}. The only source faces visible in this projection are $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$, together with the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. No host minimum, choice coordinate, quotient equality, selected limit, or Real-completeness coordinate is part of the carrier source.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRadiusCarrierSource}
\begin{proof}
Project the carrier through the ledger definition. \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger} lists the finite rows $D,W,\lambda,M,S,Q,R,H,C,P,N$ and names the dyadic cover, rational-ball radius, dyadic mesh, stream-name, regular-rational, Real, transport, continuation, provenance, and local naming faces.

Now use the root radius-window obligation surface. \autoref{thm:finite-lebesgue-number-root-radius-window-obligation-surface} states that an accepted ledger discharges the positive-radius and finite-window obligations only through those displayed rows.

The L10 source faces are therefore read as the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ part of the same finite packet, while $\DyadicCoverUp$, $\RationalBallUp$, and $\DyadicMeshUp$ supply the local radius carrier. Since neither the definition nor the surface theorem contains a row for a host minimum, choice, quotient equality, selected limit, or Real completeness, no such coordinate can appear in the projected carrier source.
\end{proof}

\begin{theorem}[Finite Lebesgue-number radius classifier stability]
\label{thm:finite-lebesgue-number-radius-classifier-stability}
Let two accepted $\FiniteLebesgueNumberUp$ root radius-window ledgers agree componentwise by $\hsame$ on the rows $D,W,\lambda,M,S,Q,R,H,C,P,N$. Then the positive-radius window transported between them has the same classifier at every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ endpoint, and the transport does not change the L10 source faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRadiusClassifierStability}
\begin{proof}
Start with the componentwise agreement. \autoref{thm:finite-lebesgue-number-root-radius-window-transport} transports the accepted radius-window obligation along the shared rows $D,W,\lambda,M,S,Q,R,H,C,P,N$ and keeps the consumer-facing surface finite.

Next apply open Phase exhaustion. \autoref{thm:finite-lebesgue-number-open-phase-radius-window-exhaustion} says that the positive-radius and finite-window reads are exhausted by the root radius-window packet before a compact, compact-net, continuous-map, or uniform-modulus endpoint can add a further coordinate.

Finally use RegSeq-StreamName nonescape. \autoref{thm:finite-lebesgue-number-regseq-streamname-nonescape} keeps the stream-name and regular-rational source faces attached to the four-face route, so the transported classifier cannot replace the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ faces. The classifier is stable because every visible row is carried by the same componentwise $\hsame$ transport.
\end{proof}

\begin{theorem}[Finite Lebesgue-number radius ledger exactness]
\label{thm:finite-lebesgue-number-radius-ledger-exactness}
The local $\NameCert$ ledger for the $\FiniteLebesgueNumberUp$ root radius-window obligation is exactly the carrier-source and classifier-stability package of \autoref{thm:finite-lebesgue-number-radius-carrier-source} and \autoref{thm:finite-lebesgue-number-radius-classifier-stability}. It has no additional compactness, choice, selected-limit, quotient, metric-completeness, or Real-completeness coordinate beyond the rows of \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger}.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRadiusLedgerExactness}
\begin{proof}
First read the carrier-source side. \autoref{thm:finite-lebesgue-number-radius-carrier-source} identifies the carrier projection with the finite rows $D,W,\lambda,M,S,Q,R,H,C,P,N$ and excludes off-ledger minima, choice, quotient equality, selected limits, and Real completeness.

Next read the classifier side. \autoref{thm:finite-lebesgue-number-radius-classifier-stability} transports the positive-radius classifier through componentwise $\hsame$ while keeping the L10 source faces fixed.

Now apply consumer exactness and Real-source coverage. \autoref{thm:finite-lebesgue-number-root-radius-window-consumer-exactness} states that every downstream compact, compact-net, continuous-map, and uniform-modulus consumer receives exactly the ledger rows, while \autoref{thm:finite-lebesgue-number-real-source-ledger-coverage} accounts for the Real-side source faces inside the same finite packet.

These two readings exhaust the local $\NameCert$ ledger: the carrier source gives the rows, classifier stability gives their transported public read, and the consumer and Real-source theorems rule out any extra compactness, choice, selected-limit, quotient, metric-completeness, or Real-completeness coordinate.
\end{proof}

\begin{theorem}[Finite Lebesgue-number root radius-window transport]
\label{thm:finite-lebesgue-number-root-radius-window-transport}
Let two accepted $\FiniteLebesgueNumberUp$ routes agree on the rows $D,W,\lambda,M,S,Q,R,H,C,P,N$ of the root radius-window obligation ledger. Then the radius-window obligation transported to $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, or $\UniformModulusUp$ consumers is the same finite obligation surface in both routes. The transport uses only $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and $\NameCert$ rows over $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootRadiusWindowTransport\_certificate}
\begin{proof}
First read the shared ledger rows. Agreement on $D,W,\lambda,M,S,Q,R$ fixes the dyadic cover, finite window, positive radius, mesh, stream-name, regular-rational, and Real endpoint data.

Use the NameCert obligations to transport componentwise. \autoref{thm:finite-lebesgue-number-namecert-obligations} keeps the carrier rows under $\hsame$, and \autoref{thm:finite-lebesgue-number-window-coverage-exactness} keeps the window witness attached to the same stream, regular-rational, Real, mesh, and cover route.

Next use the L10 and Phase Real source locks. \autoref{thm:finite-lebesgue-number-l10-source-lock} identifies the only source of the radius as the finite dyadic Real-phase route, and \autoref{thm:finite-lebesgue-number-phase-real-source-lock} makes that route visible to compact and continuous consumers without adding an outside coordinate.

The remaining rows $H,C,P,N$ replay and name the same finite packet for both routes. Therefore the transported consumer obligation is identical, because no open-cover compactness, host minimum, choice, quotient equality, selected limit, or Real-completeness coordinate can distinguish the two routes.
\end{proof}

\begin{theorem}[Finite Lebesgue-number root radius-window consumer exactness]
\label{thm:finite-lebesgue-number-root-radius-window-consumer-exactness}
Every $\CompactMetricUp$, $\CompactNetModulusSelectorUp$, $\ContinuousMapUp$, and $\UniformModulusUp$ consumer admitted downstream of the root radius-window obligation ledger receives exactly the finite rows of \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger}. The consumer receives no additional open-cover compactness, host minimum, choice, quotient equality, selected limit, or Real-completeness coordinate beyond the $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.
\end{theorem}
\begin{proof}
Start with the root obligation surface theorem above. It states that the positive radius and finite-window obligations are already exhausted by $D,W,\lambda,M,S,Q,R,H,C,P,N$.

Apply the Phase Real source lock. \autoref{thm:finite-lebesgue-number-phase-real-source-lock} makes every consumer-facing radius read pass through $\DyadicCoverUp$, $\RationalBallUp$, $\DyadicMeshUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ before any compact, compact-net, continuous-map, or uniform-modulus endpoint can inspect it.

Use the L10 source lock and window coverage exactness to cover the finite-window side. \autoref{thm:finite-lebesgue-number-l10-source-lock} fixes the source route, while \autoref{thm:finite-lebesgue-number-window-coverage-exactness} sends each accepted finite-window read through the named stream, regular-rational, Real, mesh, and cover rows.

Finally read consumer exactness from the absence of outside rows in the ledger. Since \autoref{def:finite-lebesgue-number-root-radius-window-obligation-ledger} lists only the displayed finite packet, each downstream consumer receives exactly that packet and no compactness, equality, choice, selected-limit, or completeness coordinate outside it.
\end{proof}
\leanchecked{BEDC.Derived.FiniteLebesgueNumberUp.FiniteLebesgueNumberRootRadiusWindowConsumerExactness}
