\begin{theorem}[GapClosureBoundary root router exactness]
\label{thm:gap-closure-boundary-router-exactness}
For every accepted $\GapClosureBoundaryUp$ packet $B=(G,S,R,H,C,P,N)$ of \autoref{def:gap-closure-boundary-carrier}, the root router exposes exactly two accepted routes for the hard-problem sibling consumers named in \autoref{thm:gap-closure-boundary-namecert-obligations}: the displayed source route from $G$ to $S$, and the refusal-ledger route from $G$ to $R$. Every accepted consumer route is one of these two routes over $H,C,P,N$, and no hidden closure branch, hidden $\mathsf{T}$ supply, private-access row, causal-necessity row, or aspect-reduction row is exported.
\end{theorem}
\begin{proof}
Project the accepted carrier using \autoref{def:gap-closure-boundary-carrier}. The packet contains the request row $G$, source row $S$, refusal row $R$, and the structural rows $H,C,P,N$.

Use \autoref{thm:gap-closure-boundary-namecert-obligations} to read the router surface. Its source-route exactness clause accounts for the displayed route from $G$ to $S$, and its refusal-ledger routing clause accounts for the route from $G$ to $R$.

Finally apply \autoref{thm:gap-closure-boundary-refusal-nonescape}. Since an off-source request is retained by $R$ and the structural rows only transport, route, package, and name the same packet, the router has no third accepted branch outside $G,S,R,H,C,P,N$.
\end{proof}

\begin{theorem}[GapClosureBoundary consumer route totality]
\label{thm:gap-closure-boundary-consumer-route-totality}
Every accepted read of a $\GapClosureBoundaryUp$ packet by $\CausalCommitmentUp$, $\FiniteWitnessedRefutationUp$, $\OtherMindsCommitmentUp$, $\AspectChainUp$, or $\SolipsismGapRefusalUp$ is total over the displayed source/refusal split. A supported read factors through $G \longrightarrow S$ with $H,C,P,N$, an unsupported closure request factors through $G \longrightarrow R$ with $H,C,P,N$, and no listed consumer receives a route that bypasses both $S$ and $R$.
\end{theorem}
\begin{proof}
Begin with the sibling list in \autoref{thm:gap-closure-boundary-namecert-obligations}. The listed consumers are exactly the hard-problem consumers for which the boundary packet records provenance and local naming.

For supported reads, use \autoref{thm:gap-closure-boundary-source-route-totality}. It requires the displayed route from $G$ to $S$ before any listed sibling consumes the structural rows.

For unsupported closure requests, use \autoref{thm:gap-closure-boundary-refusal-route-exactness}. It sends the request through $G \longrightarrow R$ with the same $H,C,P,N$ rows and excludes hidden closure, hidden $\mathsf{T}$ supply, and off-packet continuation.

The two cases cover the consumer ledger by \autoref{thm:gap-closure-boundary-consumer-ledger-exhaustion}. Hence every accepted sibling route is total over the source/refusal split and no consumer-specific route remains.
\end{proof}

\begin{theorem}[GapClosureBoundary refusal ledger stability]
\label{thm:gap-closure-boundary-refusal-ledger-stability}
For every accepted $\GapClosureBoundaryUp$ packet $B=(G,S,R,H,C,P,N)$, replay along $C$ and transport along $H$ preserve the refusal ledger endpoint $R$ for every unsupported hard-problem consumer request. The rows $P,N$ may package and locally name that endpoint, but they cannot turn the refusal ledger into displayed source routing, internal closure, a hidden $\mathsf{T}$ supply, or a consumer-specific continuation.
\end{theorem}
\begin{proof}
Start with \autoref{thm:gap-closure-boundary-refusal-nonescape}. An unsupported closure request has no displayed route through $S$, so the accepted continuation sends it to the refusal row $R$.

Apply \autoref{thm:gap-closure-boundary-refusal-ledger-routing} and \autoref{thm:gap-closure-boundary-structural-exhaustion}. They identify $H,C,P,N$ as the transport, route, provenance, and local naming rows for the same refusal endpoint, not as generators of another source or closure coordinate.

The consumer route totality theorem then fixes the downstream alternatives. Since every accepted read is either the displayed source route or the refusal-ledger route, a replayed unsupported request remains at $R$ and cannot become a hidden third route.
\end{proof}
