\begin{theorem}[GapClosureBoundary root certificate-gate factorization]
\label{thm:gap-closure-boundary-root-certificate-gate-factorization}
For every accepted $\GapClosureBoundaryUp$ root carrier $B=(G,S,R,H,C,P,N)$, any certificate-gate read consumed by $\CausalCommitmentUp$, $\FiniteWitnessedRefutationUp$, $\OtherMindsCommitmentUp$, $\AspectChainUp$, or $\SolipsismGapRefusalUp$ factors through the displayed source/refusal split
$$
G \longrightarrow S
\qquad\text{or}\qquad
G \longrightarrow R
$$
and then through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\GapClosureBoundaryUp}$ rows $H,C,P,N$. The factorization exports no hidden T supply, host equality, quotient row, or private selector.
\end{theorem}
\begin{proof}
Start from the accepted carrier $B=(G,S,R,H,C,P,N)$ and the existing carrier definition. The only public boundary rows are the source branch $G \longrightarrow S$, the refusal branch $G \longrightarrow R$, and the structural rows $H,C,P,N$.

Use the NameCert obligation surface and route-completion obligations. They require the certificate gate to read carrier admission, source/refusal exactness, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before any downstream consumer receives the boundary.

Finally apply consumer ledger exhaustion for the hard-problem readers. Since the ledger names only the five downstream consumers and routes each of them through the same source/refusal split, there is no remaining coordinate for hidden supply, host equality, quotient data, or private selection.
\end{proof}

\begin{theorem}[GapClosureBoundary hard-problem consumer coverage]
\label{thm:gap-closure-boundary-hard-problem-consumer-coverage}
The root carrier $B=(G,S,R,H,C,P,N)$ covers the hard-problem consumers $\CausalCommitmentUp$, $\FiniteWitnessedRefutationUp$, $\OtherMindsCommitmentUp$, $\AspectChainUp$, and $\SolipsismGapRefusalUp$ exactly through the accepted source branch $G \longrightarrow S$ and the accepted refusal branch $G \longrightarrow R$. Each consumer receives its boundary as a $\BHist$ read transported by $\hsame$, replayed by $\Cont$, packaged by $\Pkg$, and named by $\NameCert_{\GapClosureBoundaryUp}$.
\end{theorem}
\begin{proof}
First read the consumer ledger exhaustion theorem for the root packet. It lists the hard-problem consumers and assigns their supported requests to the source branch and their unsupported requests to the refusal branch.

Next use the recognizer landing obligations. A consumer that lands positively must pass through the source row $S$, while a consumer that fails to land remains on the refusal row $R$. Both landings are still reads of the same carrier $B$.

The status block records the chapter commitment for the same carrier. Combining it with the displayed route rows $H,C,P,N$ shows that coverage is by the finite certificate gate alone, not by a hidden supply, host equality, quotient row, or private selector.
\end{proof}

\begin{theorem}[GapClosureBoundary TasteGate obligation triad]
\label{thm:gap-closure-boundary-tastegate-obligation-triad}
For the accepted carrier $B=(G,S,R,H,C,P,N)$, a future TasteGate proof for $\GapClosureBoundaryUp$ must discharge exactly the root carrier admission, source/refusal branch exactness, and hard-problem consumer coverage obligations. These obligations are expressed through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\GapClosureBoundaryUp}$ rows and do not add a hidden T supply, host equality, quotient row, or private selector.
\end{theorem}
\begin{proof}
Carrier admission is the first obligation. It exposes $G,S,R,H,C,P,N$ as the only accepted rows of the root packet.

Source/refusal exactness is the second obligation. The source branch $G \longrightarrow S$ handles supported recognizer landings, and the refusal branch $G \longrightarrow R$ handles unsupported closure requests.

Hard-problem consumer coverage is the third obligation. The preceding coverage theorem routes $\CausalCommitmentUp$, $\FiniteWitnessedRefutationUp$, $\OtherMindsCommitmentUp$, $\AspectChainUp$, and $\SolipsismGapRefusalUp$ through the same carrier, so the triad exhausts the certificate-gate obligations needed by the TasteGate surface.
\end{proof}
