\begin{theorem}[GapClosureBoundary root recognizer admission totality]
\label{thm:gap-closure-boundary-root-recognizer-admission-totality}
For every accepted $\GapClosureBoundaryUp$ carrier $B=(G,S,R,H,C,P,N)$, every root recognizer admission that reaches a downstream hard-problem consumer must first pass through the $\GroundCompilerRecognizerFlowUp$ acceptance route and then land in the displayed $\FiniteReflectionTupleUp$ image. The admitted branch is consumed as the source route $G \longrightarrow S$ with the displayed transport, continuation, provenance, and local naming rows; no hidden source selector, private compiler state, or off-packet recognition channel is exported.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:gap-closure-boundary-carrier}. The root boundary exposes only the packet $G,S,R,H,C,P,N$.

Apply recognizer source admission, \autoref{thm:gap-closure-boundary-recognizer-source-admission}. It forces successful recognizer evidence through $\GroundCompilerRecognizerFlowUp$ and then through the $\FiniteReflectionTupleUp$ tuple image before the boundary packet is consumed.

Finally use admission route totality, \autoref{thm:gap-closure-boundary-admission-route-totality}. The accepted branch is the displayed $G \longrightarrow S$ route under $H,C,P,N$, so no hard-problem consumer receives an additional source coordinate.
\end{proof}

\begin{theorem}[GapClosureBoundary root refusal ledger coverage]
\label{thm:gap-closure-boundary-root-refusal-ledger-coverage}
For every accepted $\GapClosureBoundaryUp$ carrier $B=(G,S,R,H,C,P,N)$, every root recognizer request that fails to land through the $\GroundCompilerRecognizerFlowUp$ and $\FiniteReflectionTupleUp$ admission route is covered by the displayed refusal ledger $R$. The GAP residue available to downstream hard-problem consumers is therefore the finite refusal branch $G \longrightarrow R$ with the same $H,C,P,N$ structural rows, not hidden closure supply, host equality, quotient data, private source access, or an off-packet continuation.
\end{theorem}
\begin{proof}
Begin with recognizer refusal stability, \autoref{thm:gap-closure-boundary-recognizer-refusal-stability}. A failed tuple landing cannot be reread as accepted source evidence, so the request is routed to the refusal ledger.

Use refusal route stability, \autoref{thm:gap-closure-boundary-refusal-route-stability}. The rows $H,C,P,N$ preserve the endpoint $R$ and package it as the displayed GAP residue rather than replacing it with another route.

The coverage is exhaustive by consumer readiness exhaustion, \autoref{thm:gap-closure-boundary-consumer-readiness-exhaustion}. Unsupported closure requests for the listed hard-problem consumers remain inside the same refusal branch.
\end{proof}

\begin{theorem}[GapClosureBoundary root NameCert consumer exhaustion]
\label{thm:gap-closure-boundary-root-namecert-consumer-exhaustion}
For the downstream consumers $\CausalCommitmentUp$, $\FiniteWitnessedRefutationUp$, $\OtherMindsCommitmentUp$, $\AspectChainUp$, and $\SolipsismGapRefusalUp$, the root $\GapClosureBoundaryUp$ NameCert surface is exhausted by the displayed source row, refusal ledger, transport rows, continuation routes, package provenance, and local naming row of $B=(G,S,R,H,C,P,N)$. A consumer may read admitted source evidence through $G \longrightarrow S$ or refusal coverage through $G \longrightarrow R$, but it receives no separate hard-problem carrier, hidden closure oracle, host-level equality, or unnamed route.
\end{theorem}
\begin{proof}
First assemble the accepted branch. By \autoref{thm:gap-closure-boundary-root-recognizer-admission-totality}, recognizer admission reaches the boundary only as the displayed source route $G \longrightarrow S$.

Next assemble the refusal branch. By \autoref{thm:gap-closure-boundary-root-refusal-ledger-coverage}, every failed or unsupported recognizer request is carried by $G \longrightarrow R$ under the same structural rows.

It remains to account for the consumer surface. Apply recognizer consumer exhaustion, \autoref{thm:gap-closure-boundary-recognizer-consumer-exhaustion}, and consumer readiness exhaustion, \autoref{thm:gap-closure-boundary-consumer-readiness-exhaustion}. Together they show that the listed hard-problem consumers read only $G,S,R,H,C,P,N$ and no sibling-specific or off-packet NameCert row.
\end{proof}
