\begin{theorem}[GapClosureBoundary scoped source-refusal record]
\label{thm:gap-closure-boundary-scoped-source-refusal-record}
For every accepted $\GapClosureBoundaryUp$ carrier
$$
B=(G,S,R,H,C,P,N),
$$
the scoped source-refusal record is exactly the finite $\BHist$ packet with the source route $G \longrightarrow S$, the refusal route $G \longrightarrow R$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local $\NameCert_{\GapClosureBoundaryUp}$ row $N$. The record contains no third route, hidden source selector, internal closure coordinate, or off-packet consumer row.
\end{theorem}
\begin{proof}
Start with the carrier and local NameCert obligations, \autoref{def:gap-closure-boundary-carrier} and \autoref{thm:gap-closure-boundary-namecert-obligations}. They expose $G,S,R,H,C,P,N$ as the finite carrier inventory and assign $H,C,P,N$ to transport, replay, provenance, and naming.

For the source side, apply source-route totality, \autoref{thm:gap-closure-boundary-source-route-totality}. Every supported read reaches the displayed source row through $G \longrightarrow S$ before the structural rows are consumed.

For the refusal side, apply refusal-route exactness, \autoref{thm:gap-closure-boundary-refusal-route-exactness}. Every unsupported read reaches $R$ through $G \longrightarrow R$ with the same structural rows.

Finally use consumer ledger exhaustion, \autoref{thm:gap-closure-boundary-consumer-ledger-exhaustion}. Since the two displayed branches exhaust the listed consumers, the scoped record has no third route or hidden closure coordinate.
\end{proof}

\begin{theorem}[GapClosureBoundary consumer scope nonescape]
\label{thm:gap-closure-boundary-consumer-scope-nonescape}
Every accepted $\GapClosureBoundaryUp$ consumer route factors through the scoped source-refusal record of \autoref{thm:gap-closure-boundary-scoped-source-refusal-record}. Supported consumers read $G \longrightarrow S$ with $H,C,P,N$, unsupported consumers read $G \longrightarrow R$ with $H,C,P,N$, and no consumer can read host equality, quotient data, private other-minds access, causal necessity, direct aspect reduction, hidden $\mathsf{T}$ supply, or an off-packet continuation.
\end{theorem}
\begin{proof}
First invoke the scoped source-refusal record. It fixes the only accepted carrier rows and the two displayed branches before a downstream hard-problem consumer receives the packet.

Next apply the consumer exactness package, \autoref{thm:gap-closure-boundary-consumer-exactness-package}. It keeps the listed sibling consumers on the same shared boundary carrier rather than on consumer-specific source, refusal, transport, continuation, provenance, or naming coordinates.

Finally use refusal non-escape and structural row conservation, \autoref{thm:gap-closure-boundary-refusal-nonescape} and \autoref{thm:gap-closure-boundary-structural-row-conservation}. The refusal branch cannot become a closure supply, and the structural rows preserve the displayed branch instead of creating host equality, quotient data, private access, causal necessity, aspect reduction, hidden $\mathsf{T}$ data, or an off-packet continuation.
\end{proof}

\begin{theorem}[GapClosureBoundary TasteGate scope readback]
\label{thm:gap-closure-boundary-tastegate-scope-readback}
The TasteGate readback for $\GapClosureBoundaryUp$ reads exactly the scoped source-refusal record over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It preserves the carrier $B=(G,S,R,H,C,P,N)$, the source route $G \longrightarrow S$, the refusal route $G \longrightarrow R$, consumer factorization, and the rows $H,C,P,N$ as the complete transport, replay, provenance, and local naming surface for the accepted boundary.
\end{theorem}
\begin{proof}
Begin with the scoped source-refusal record and consumer scope nonescape. These results bind the carrier, source branch, refusal branch, and downstream consumer routes to $G,S,R,H,C,P,N$.

Use the TasteGate obligation triad, \autoref{thm:gap-closure-boundary-tastegate-obligation-triad}. It reads the same carrier exposure, branch distinction, and structural rows as the visible packet whose nontriviality is recorded by the TasteGate target.

Close with the NameCert scope readiness theorem, \autoref{thm:gap-closure-boundary-namecert-scope-readiness}. Its readback surface is precisely $\BHist$ carrier data, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row, so the TasteGate readback cannot add an external source, refusal, or consumer coordinate.
\end{proof}
