\subsection{Wittgenstein and use}
\label{subsec:philosophy-wittgenstein-use}

\begin{definition}[Use and rule question]
\label{def:philosophy-use-rule-question}
The Wittgenstein-style question links meaning to use and rule-following
to public practice. In BEDC it lands on licensed use under
\(\NameCert\) and classifier-stable continuation with a ledger.
\end{definition}

\begin{definition}[BEDC use]
\label{def:philosophy-bedc-use}
A use of a name \(N\) is legitimate when the item used falls under the
source and classifier fields of \(N\), the use is stable under the
stability certificate, and hidden material is tracked by the ledger
policy.
\end{definition}

\begin{theorem}[Meaning is certified use]
\label{thm:philosophy-meaning-certified-use}
In BEDC, the meaning of a name is given by its auditable use rules.
\end{theorem}
\begin{proof}
The naming certificate states source, pattern, classifier, stability,
and ledger fields. Without these fields the name is not licensed.
Meaning is therefore neither private image nor bare reference, but
certificate-governed use.
\end{proof}

\begin{corollary}[Rule-following is audited, not merely social]
\label{cor:philosophy-rule-following-audited}
BEDC is adjacent to the public-checkability side of rule-following, but
its use is classifier-, witness-, ledger-, and stability-governed
rather than ordinary social habit.
\end{corollary}
\begin{proof}
Social practices can drift and remain implicit. BEDC public use must
be auditable by certificate fields.
\end{proof}

\subsection{Whitehead and process}
\label{subsec:philosophy-whitehead-process}

\begin{definition}[Process question]
\label{def:philosophy-process-question}
The process-philosophy question says that reality is process rather
than static substance. Its BEDC landing site is \(\Cont\) as universal
verb, history growth, and naming certificates as stabilized
process-interfaces.
\end{definition}

\begin{definition}[BEDC process]
\label{def:philosophy-bedc-process}
A BEDC process is a displayed continuation \(\Cont(h,d,h')\) and its
specializations under certificates: observation, time step,
computation, morphism, type checking, or continuity modulus.
\end{definition}

\begin{theorem}[BEDC is certificate process theory]
\label{thm:philosophy-bedc-certificate-process-theory}
BEDC is structurally adjacent to process philosophy in that continuation
precedes mature objecthood.
\end{theorem}
\begin{proof}
Distinction and history precede objects. Observation and time are
continuation readings. Mature objects are names licensed after stable
continuation behavior has been classified and ledgered. Objecthood is
therefore downstream from process.
\end{proof}

\begin{corollary}[BEDC is not Whiteheadian metaphysics]
\label{cor:philosophy-bedc-not-whiteheadian}
BEDC shares process priority but does not import actual occasions,
prehension, or organic metaphysics.
\end{corollary}
\begin{proof}
Its process site is the finite continuation relation and its
certificate discipline, not a general metaphysical category.
\end{proof}

\subsection{Tarski, Godel, and Muenchhausen}
\label{subsec:philosophy-formal-limit-tradition}

\begin{definition}[Formal-limit tradition]
\label{def:philosophy-formal-limit-tradition}
The formal-limit tradition includes incompleteness, undefinability,
bootstrap impossibility, and halting undecidability. Its BEDC landing
site is the closed-ground-loop and open-meta-loop architecture.
\end{definition}

\begin{theorem}[Limit results are open-meta-loop phenomena]
\label{thm:philosophy-limit-results-open-meta-loop}
BEDC reads incompleteness, undefinability, bootstrap impossibility, and
halting obstruction as different faces of the open meta loop.
\end{theorem}
\begin{proof}
The ground loop must close so generation can begin. The meta loop must
remain open so the system does not internalize total truth, runtime, or
halting decision. The limit phenomena arise when a system attempts to
close the latter.
\end{proof}

\begin{corollary}[BEDC does not bypass formal limits]
\label{cor:philosophy-bedc-does-not-bypass-limits}
BEDC does not claim to overcome formal limits; it isolates the minimal
ground closure required for formal systems while refusing meta closure.
\end{corollary}
\begin{proof}
The primitive distinction is the ground payment. Truth and runtime
remain outside the object layer. This exposes the boundary rather than
removing it.
\end{proof}

\begin{corollary}[Reflection is not a strange loop]
\label{cor:philosophy-reflection-not-strange-loop}
BEDC self-description is layered reflection, not a collapse of the
describing and described layers.
\end{corollary}
\begin{proof}
Collapsing the two layers would recreate the truth-totalization
problem. BEDC keeps structural description, described structure, and
external checking distinct.
\end{proof}

\concretizedIn{ch:concrete-instances-useprocesslimit-namecert}{UseProcessLimitUp realizes certified use, rule audit, continuation process, and formal-limit refusal as one finite NameCert packet.}
\concretizedIn{ch:concrete-instances-use-process-limit-ledger-namecert}{Use-process-limit ledgers realize certified use, continuation-process, and formal-limit refusal as one finite NameCert packet.}
