\subsection{Hard problems as closure questions}
\label{subsec:philosophy-hard-problems-closure-questions}

\begin{definition}[BEDC hard problem form]
\label{def:philosophy-hard-problem-form}
A hard problem in BEDC asks which records are generated, which choices
are ledgered, which compressions preserve provenance, which relations
have finite witnesses, which invariants are classifier-stable, and
which pressures remain exposed as gap or \(T\)-boundary readings.
\end{definition}

\begin{theorem}[Hard problems become closure questions]
\label{thm:philosophy-hard-problems-closure-questions}
Within a closed records-side frame, traditional hard problems about
consciousness, universe, observer, time, space, and identity become
boundary questions about finite carriers.
\end{theorem}
\begin{proof}
The object layer can inspect records, ledgers, relations, invariants,
and gap rows. It cannot close the corresponding traditional essence
questions by adding new primitives. The problems are therefore
translated into questions of generated records, transport, stability,
and exposed boundary pressure.
\end{proof}

\begin{corollary}[Traditional questions receive records-side rewrites]
\label{cor:philosophy-traditional-questions-records-rewrites}
Consciousness becomes focused self-tracking history; universe becomes a
finite horizon slice; time becomes local continuation; space becomes
locality-cell geometry; identity becomes \(\hsame\)-stable trace; and
the God's-eye view becomes a refused global synchronization.
\end{corollary}

\subsection{Causality as forward binding}
\label{subsec:philosophy-causality-forward-binding}

\begin{definition}[Causal commitment]
\label{def:philosophy-causal-commitment}
A causal commitment of a conscious observational system is a gap tag
whose content is that an observed regularity persists into
not-yet-observed continuation.
\end{definition}

\begin{theorem}[Causality is not primitive law]
\label{thm:philosophy-causality-not-primitive-law}
In BEDC, causality is not a substrate-internal primitive law; it is a
Type IV forward-binding commitment.
\end{theorem}
\begin{proof}
Finite records can show observed regularity and prediction history.
They do not generate universal future persistence. Treating the
regularity as future law is therefore a gap-tagged causal commitment.
\end{proof}

\begin{corollary}[Scientific theories are records plus gap stack]
\label{cor:philosophy-scientific-theories-records-gap-stack}
A scientific theory, in BEDC terms, consists of empirical records,
regularity summaries, gap-tagged future-persistence commitments, and
possible refutation rows.
\end{corollary}
\begin{proof}
The records and summaries are visible in the ledger. The projection to
future cases exceeds the current record and is held as a Type IV
socket.
\end{proof}

\subsection{Free will as inscription event}
\label{subsec:philosophy-free-will-inscription-event}

\begin{definition}[Inscription event]
\label{def:philosophy-phenomenology-inscription-event}
An inscription event is a transition \(O_t\unrhd O_{t+1}\) in which
new records enter a conscious observational system and the arrival of
those records is read as local actualization of \(T\) at the
inscription point.
\end{definition}

\begin{definition}[Free will]
\label{def:philosophy-free-will}
Free will is the inscription-event aspect of conscious accumulation:
the aspect under which new records arrive as inscriptions rather than
as a separate faculty inhabiting the system.
\end{definition}

\begin{theorem}[Free will is not a faculty]
\label{thm:philosophy-free-will-not-faculty}
Free will is not an additional power or substance attached to the
system; it is an aspect of the accumulation chain.
\end{theorem}
\begin{proof}
Adding a faculty would introduce a new carrier and transport surface.
The BEDC reading instead identifies the event by which records enter a
local history as the relevant aspect.
\end{proof}

\begin{corollary}[Freedom is compatible with records-side determinism]
\label{cor:philosophy-freedom-compatible-determinism}
Records-side determinism does not eliminate inscription-event novelty.
\end{corollary}
\begin{proof}
A derivation may be replayed or checked deterministically on the
records side. The actuality of that row entering a local history is
read at a different aspect-position.
\end{proof}

\begin{example}[Mathematical creation]
\label{ex:philosophy-mathematical-creation-inscription}
The arrival of a theorem row after a visible gap and selected route can
be read as an inscription event. The proof route may be mechanized; the
event of the route becoming public record is the inscription aspect.
\end{example}

\subsection{Other minds and cross-perspective alignment}
\label{subsec:philosophy-other-minds-cross-perspective}

\begin{definition}[Other-minds commitment]
\label{def:philosophy-other-minds-commitment}
An other-minds commitment is a gap-tagged locality-cell commitment that
treats external records of another system as records of another
conscious observational system.
\end{definition}

\begin{theorem}[Other minds are locality-cell commitments]
\label{thm:philosophy-other-minds-locality-cell-commitments}
BEDC does not directly observe another self; it records behavior and
may issue a gap-tagged locality-cell commitment that the behavior
belongs to another closed observational system.
\end{theorem}
\begin{proof}
The records side can contain communication, behavior, and coordination
rows. The recognition of another inscription-bearing history is an
additional Type V commitment rather than a direct record of another
self.
\end{proof}

\begin{corollary}[Solipsism is commitment refusal]
\label{cor:philosophy-solipsism-commitment-refusal}
Solipsism is not a BEDC refutation theorem; it is the refusal to issue
other-minds locality commitments.
\end{corollary}
\begin{proof}
The substrate does not force the commitment. Refusing it remains
records-side consistent, but impoverishes the locality-cell geometry.
\end{proof}

\begin{corollary}[Collaboration uses other-minds commitment]
\label{cor:philosophy-collaboration-other-minds-commitment}
Accepting another contributor's checked record uses records-side
evidence from rechecking, while recognizing the contributor as another
inscription point is an other-minds commitment.
\end{corollary}
\begin{proof}
The checker supplies audit evidence for the row. The recognition of
another conscious observational system exceeds that evidence and is
held as locality-cell commitment.
\end{proof}

\subsection{Mind and matter as double reading}
\label{subsec:philosophy-mind-matter-double-reading}

\begin{definition}[Records-side]
\label{def:philosophy-records-side}
The records-side reading of an accumulation chain reads it as
generated records, physical measurements, observable behavior, and
ledgered dependencies.
\end{definition}

\begin{definition}[Inscription-side]
\label{def:philosophy-inscription-side}
The inscription-side reading of the same chain reads it as the arrival
of records, local actualization of \(T\), and first-person
phenomenological aspect.
\end{definition}

\begin{theorem}[Mind--matter is not a two-substance relation]
\label{thm:philosophy-mind-matter-not-two-substance}
The mind--matter relation in BEDC is not a relation between two
substances, but two readings of one accumulation chain.
\end{theorem}
\begin{proof}
The records-side account and inscription-side account apply to the
same transition. One reads measured dependencies and observable rows;
the other reads the actuality of record arrival at an inscription
point. No second substance is added.
\end{proof}

\begin{corollary}[Neural correlate and thought are double readings]
\label{cor:philosophy-neural-correlate-thought-double-reading}
A measured neural correlate and the corresponding thought are not two
objects joined by a hidden relation, but records-side and
inscription-side readings of the same accumulation event.
\end{corollary}
\begin{proof}
The measurement belongs to the records-side ledger. The thought belongs
to the inscription-side reading of the same local transition.
\end{proof}

\subsection{Self-reference as gap-on-gap}
\label{subsec:philosophy-self-reference-gap-on-gap}

\begin{definition}[Self-reference attempt]
\label{def:philosophy-self-reference-attempt}
A self-reference attempt records a statement about the complete record
ledger of the very state in which the statement appears.
\end{definition}

\begin{definition}[Gap-on-gap hierarchy]
\label{def:philosophy-gap-on-gap-hierarchy}
A gap-on-gap hierarchy arises when a record about a current observation
ledger becomes part of the next ledger, requiring a further record
about the enlarged ledger, and so on.
\end{definition}

\begin{theorem}[Self-reference does not close]
\label{thm:philosophy-self-reference-does-not-close}
Complete self-reference cannot close as a gap-free record in BEDC; it
appears as a hierarchy of gaps about gaps.
\end{theorem}
\begin{proof}
A statement about the complete current ledger becomes a new record when
entered. The new ledger differs from the ledger described. Recording
that difference creates another layer, so complete closure is displaced
into a hierarchy.
\end{proof}

\begin{corollary}[Russell-style closure is refused]
\label{cor:philosophy-russell-style-closure-refused}
A record whose content negates its own presence in the observation
ledger cannot become a gap-free closed record.
\end{corollary}
\begin{proof}
If the record enters the ledger, its content is false; if it does not,
it is not the displayed record it claims to be. The attempt is held as a
self-reference boundary rather than a closed object-layer fact.
\end{proof}

\subsection{Synthesis}
\label{subsec:philosophy-phenomenology-synthesis}

\begin{theorem}[Phenomenological framework synthesis]
\label{thm:philosophy-phenomenological-framework-synthesis}
BEDC rewrites consciousness, universe, time, space, identity,
causality, freedom, other minds, mind--matter relation, and
self-reference as focused records-side carrier, finite
observation-history slice, local continuation chain, locality-cell
geometry, \(\hsame\)-stable trace, Type IV gap, Type VI inscription
event, Type V locality commitment, double reading of one accumulation
chain, and Type VII gap-on-gap hierarchy.
\end{theorem}
\begin{proof}
The focused multi-history ledger supplies the finite carrier.
Consciousness is read through the focused history and self-proxy.
Universe is a finite slice of admitted histories. Time is local
continuation. Space is graph-like inter-history locality. Identity is
history-sameness-stable trace continuity. Causality, freedom, other
minds, and self-reference align with the corresponding socket types.
Mind and matter are two readings of the same accumulation chain.
\end{proof}

\begin{corollary}[No added phenomenological primitives]
\label{cor:philosophy-no-added-phenomenological-primitives}
This framework adds no primitive consciousness substance, global
universe, absolute time, spatial substrate, self entity, causal-law
primitive, free-will faculty, direct access to other minds, mental
substance, or truth totalizer.
\end{corollary}

\begin{corollary}[Passage to scientific objects]
\label{cor:philosophy-passage-to-scientific-objects}
The next layer may treat scientific and physical terms by asking which
are records-side carriers, which are schema horizons, which require
naming certificates, and which remain gap or \(T\)-boundary readings.
\end{corollary}
