\subsection{Vision: Materiality as Orbit-Closure and Freedom-like Appearance as Orbit-Escape}
\label{subsec:philosophy-materiality-orbit-escape}

\begin{remark}[VisionSeed status]
\label{rem:philosophy-materiality-orbit-escape-status}
This interface has status VisionSeed, schema-only horizon, and no Lean
target. It is not a finite-kernel theorem. It records the certificate
shape a later development would have to close before materiality,
agency-like appearance, or observer-relative feedback could be reported
as a BEDC theorem.
\end{remark}

The schema uses only the current BEDC reading that observer identity is
internal to $\Hist$, that $\Cont$ has only history-valued arguments, and
that no observer-substance stands behind the generated trace. The
observer is the history value read modulo $\hsame$, while observation,
distinction, and local time-step share the continuation form. A
derived interface entering this vocabulary must therefore be licensed
through the ordinary naming-certificate discipline:
$$
\NameCert(N)=
(\SourceSpec{}_{N},\PatternSpec{}_{N},\ClassifierSpec{}_{N},
\StabCert{}_{N},\LedgerPolicy{}_{N}).
$$
The interface below is not a primitive object and does not add a
subject parameter to the kernel.

\begin{definition}[Observational context]
\label{def:philosophy-observational-context}
An observational context is a ledger-readable package
$$
\mathcal O=(h,\Pi,X,I_X,S_X,\mathcal R,L),
$$
where $h:\Hist$ is the observer-history, $\Pi$ is a repeated probe
pattern or probe bundle, $X$ is a candidate observed interface, $I_X$
is an identity classifier for feedback records of $X$, $S_X$ is a
state classifier, $\mathcal R$ is a finite family of currently
available ledger-certified orbit rules, and $L$ records the source,
pattern, classifier, stability, and hidden-provenance data required by
the relevant naming certificates.
\end{definition}

\begin{definition}[Feedback prefix]
\label{def:philosophy-feedback-prefix}
For an observational context $\mathcal O$, a feedback prefix of length
$N$ is a finite sequence
$$
F^N_{\mathcal O}(X)=(r_0,r_1,\ldots,r_N)
$$
whose entries are BEDC-visible response histories generated by
repeatedly applying $\Pi$ to $X$ as recorded in $h$. An infinite
feedback stream is admissible here only as a schema whose every finite
prefix is ledger-visible; no completed external stream is added to the
kernel.
\end{definition}

\begin{definition}[Identity closure]
\label{def:philosophy-identity-closure}
A feedback prefix $F^N_{\mathcal O}(X)=(r_0,\ldots,r_N)$ is
identity-closed in $\mathcal O$, written
$\mathsf{IdCl}^N_{\mathcal O}(F)$, when the ledger supplies positive
classifier witnesses $I_X(r_i,r_j)$ for all $0\leq i,j\leq N$.
Identity closure says that the responses may differ while remaining
traceable as responses of the same observed datum.
\end{definition}

\begin{definition}[Ledger-certified orbit rule]
\label{def:philosophy-ledger-certified-orbit-rule}
A ledger-certified orbit rule in $\mathcal O$ is a BEDC-visible
continuation and classifier pattern
$$
T:r_i\mapsto r^{\mathsf{pred}}_{i+1}
$$
licensed by a naming certificate, reuse certificate, or equivalent
certificate, preserving the relevant feedback carrier, respecting
$S_X$, and carrying ledger witnesses for the hidden source and
classifier data used by the rule.
\end{definition}

\begin{definition}[Orbit closure and certified escape]
\label{def:philosophy-orbit-closure-certified-escape}
The prefix $F^N_{\mathcal O}(X)=(r_0,\ldots,r_N)$ is orbit-closed under
$T$, written $\mathsf{OrbitCl}^N_{\mathcal O}(F,T)$, when
$$
\forall i<N,\quad S_X(r_{i+1},T(r_i))
$$
is witnessed in the ledger. It escapes the current finite rule family
$\mathcal R$, written $\mathsf{Escape}^N_{\mathcal O}(F,\mathcal R)$,
when for every $T\in\mathcal R$ there is some $i<N$ with a positive
separation witness
$$
\mathsf{Sep}_{S_X}(r_{i+1},T(r_i)).
$$
Escape is therefore not absence of prediction. It is certified
separation from each currently available orbit rule.
\end{definition}

\begin{definition}[Material and freedom-like appearance]
\label{def:philosophy-material-freedomlike-appearance}
The prefix $F^N_{\mathcal O}(X)$ has material appearance relative to
$\mathcal O$ when
$$
\mathsf{IdCl}^N_{\mathcal O}(F)
\quad\wedge\quad
\exists T\in\mathcal R,\ \mathsf{OrbitCl}^N_{\mathcal O}(F,T).
$$
It has freedom-like appearance relative to $\mathcal O$ when
$$
\mathsf{IdCl}^N_{\mathcal O}(F)
\quad\wedge\quad
\mathsf{Escape}^N_{\mathcal O}(F,\mathcal R).
$$
The phrase freedom-like is part of the schema. It does not assert
absolute metaphysical free will; it classifies observer-relative
feedback inside a finite ledger.
\end{definition}

\begin{definition}[Noise-like feedback]
\label{def:philosophy-noise-like-feedback}
A prefix is noise-like or unformed, for this schema, when the observer
lacks identity closure or when the ledger supplies a positive
identity-separation witness
$$
\exists i,j\leq N,\quad \mathsf{Sep}_{I_X}(r_i,r_j).
$$
Without traceable sameness, non-orbit-closure is not agency-like
appearance.
\end{definition}

\begin{proposition}[Schema consequences]
\label{prop:philosophy-materiality-orbit-escape-consequences}
Within a fixed observational context and finite rule family, material
appearance is identity-preserving orbit closure, freedom-like
appearance is identity-preserving certified orbit escape, and
noise-like feedback is excluded from freedom-like appearance whenever
identity classifier separation is sound. If $S_X(a,b)$ implies
$\neg\mathsf{Sep}_{S_X}(a,b)$, then the same feedback prefix cannot be
both material and freedom-like in that fixed context.
\end{proposition}
\begin{proof}
Each assertion unfolds the preceding definitions. Material appearance
contains identity closure together with an orbit-closing rule.
Freedom-like appearance contains identity closure together with
certified separation from every rule in the current finite family.
Positive identity separation contradicts identity closure when the
identity classifier is sound. If material appearance supplies
$T_0\in\mathcal R$ with $S_X(r_{i+1},T_0(r_i))$ for every $i<N$, then
freedom-like appearance would require some $i<N$ with
$\mathsf{Sep}_{S_X}(r_{i+1},T_0(r_i))$, contradicting state-classifier
separation soundness.
\end{proof}

\begin{proposition}[Rule extension changes appearance]
\label{prop:philosophy-rule-extension-appearance}
If $\mathcal R\subseteq\mathcal R'$ in the same observational context,
material appearance relative to $\mathcal R$ persists relative to
$\mathcal R'$. Freedom-like appearance need not persist.
\end{proposition}
\begin{proof}
An orbit-closing rule $T\in\mathcal R$ remains available in
$\mathcal R'$, so the same witness proves material appearance. By
contrast, $\mathcal R'$ may contain a rule $T^\ast$ absent from
$\mathcal R$ that closes the feedback orbit. The prefix then no longer
escapes every currently available rule in the enlarged context.
\end{proof}

\begin{corollary}[No context-free materiality or free-will predicate]
\label{cor:philosophy-no-context-free-materiality-freewill}
The schema licenses only context-indexed judgments such as
$\mathsf{Material}^N_{\mathcal O}(F)$ and
$\mathsf{FreedomLike}^N_{\mathcal O}(F)$. It does not license
unindexed kernel predicates $\mathsf{Material}(X)$ or
$\mathsf{FreeWill}(X)$.
\end{corollary}
\begin{proof}
The definitions require an observer-history, probe pattern, candidate
interface, identity classifier, state classifier, finite rule family,
ledger, and finite feedback prefix. Removing these parameters removes
the judgment. BEDC supplies no global observer, no context-free
classifier, and no external equality oracle.
\end{proof}

\begin{remark}[Roadmap obligations]
\label{rem:philosophy-materiality-roadmap-obligations}
Closing this horizon would require certificate fields for the feedback
carrier, the identity classifier, the state classifier, positive
separation predicates, orbit-rule stability, prefix-extension ledger
stability, and provenance of any packaging that exposes $X$ as a public
interface. Standard bridges to dynamical systems, stochastic
processes, learning theory, decision theory, or philosophy of agency
would remain interpretive until they preserve these certificate
obligations without replacing them.
\end{remark}

Materiality and freedom-like appearance are therefore not primitive
properties of an object-substance. They are observer-relative
classifications of feedback prefixes. A datum appears material when
the observer-history can track it as the same datum and close its
responses under a finite ledger-certified orbit rule. A datum appears
freedom-like when it remains identity-traceable while escaping every
currently available orbit rule. Pure irregularity is insufficient:
without identity closure, non-orbit-closure is noise or unformed data
rather than agency. The contrast is not between law and lawlessness,
but between two ledger-visible structures: orbit closure and
identity-preserving orbit escape.

\concretizedIn{ch:concrete-instances-materiality-orbit-escape-namecert}{Materiality and freedom-like appearance are realized as finite orbit-closure and certified-escape NameCert rows.}

\subsubsection{Relative Non-Domination and the Refusal of Absolute Acausality}
\label{subsubsec:philosophy-relative-non-domination}

The preceding schema also fixes the admissible reading of free-will
language. It does not introduce free will as a primitive metaphysical
substance, nor does it identify freedom with absolute acausality. The
only BEDC-legible form is indexed by an observer-history, a finite
ledger, a classifier package, a rule family, and a feedback prefix:
$$
\text{freedom-like appearance}
\quad\rightsquigarrow\quad
\text{relative non-domination by a finite observer ledger}.
$$
The index is load-bearing. A prefix may be freedom-like relative to one
observer and material relative to another when their ledgers, probes,
classifiers, and available orbit rules differ.

\begin{definition}[Ledger dominance]
\label{def:philosophy-ledger-dominance}
Let $\mathcal O_A=(A,\Pi_A,X,I_A,S_A,\mathcal R_A,L_A)$ and
$\mathcal O_B=(B,\Pi_B,X,I_B,S_B,\mathcal R_B,L_B)$ be observational
contexts for the same candidate interface $X$. The observer-history
$B$ ledger-dominates $X$ over prefix length $N$, written
$B\triangleright_N X$, when the $B$-context supplies identity closure
and an orbit-closing rule:
$$
\mathsf{IdCl}^N_{\mathcal O_B}(F_B)
\quad\wedge\quad
\exists T_B\in\mathcal R_B,\,
\mathsf{OrbitCl}^N_{\mathcal O_B}(F_B,T_B).
$$
Equivalently, $X$ has material appearance relative to the
$B$-context over that prefix.
\end{definition}

\begin{definition}[Relative non-domination]
\label{def:philosophy-relative-non-domination}
The interface $X$ is non-dominated relative to $\mathcal O_A$ over
prefix length $N$ when
$$
\mathsf{NonDom}^N_{\mathcal O_A}(X)
\quad\Longleftrightarrow\quad
\mathsf{IdCl}^N_{\mathcal O_A}(F_A)
\wedge
\mathsf{Escape}^N_{\mathcal O_A}(F_A,\mathcal R_A).
$$
Thus relative non-domination is not the absence of cause. It is the
presence of traceable sameness together with certified escape from the
finite orbit rules available to the observer ledger.
\end{definition}

\begin{definition}[Forbidden absolute predicate]
\label{def:philosophy-forbidden-absolute-freewill}
A context-free predicate $\mathsf{FreeWill}(X)$ would assert a property
of $X$ independently of observer-history, probe pattern, identity
classifier, state classifier, rule family, ledger, and prefix length.
This section does not introduce such a predicate. The admissible
judgments are indexed forms such as
$$
\mathsf{FreedomLike}^N_{\mathcal O_A}(F_A),
\quad
\mathsf{NonDom}^N_{\mathcal O_A}(X),
\quad
\mathsf{Material}^N_{\mathcal O_A}(F_A),
\quad
B\triangleright_N X.
$$
\end{definition}

\begin{proposition}[Dominance collapses freedom-like appearance in the same context]
\label{prop:philosophy-dominance-collapses-freedomlike}
Assume state-separation soundness in the $B$-context:
$$
S_B(a,b)\Rightarrow\neg\mathsf{Sep}_{S_B}(a,b).
$$
If $B\triangleright_N X$, then $X$ does not have freedom-like
appearance relative to the same $B$-context over that prefix.
\end{proposition}
\begin{proof}
By \autoref{def:philosophy-ledger-dominance}, there is some
$T_B\in\mathcal R_B$ such that
$$
\forall i<N,\quad S_B(r_{i+1},T_B(r_i)).
$$
If the same prefix were freedom-like relative to $\mathcal O_B$, then
escape from $\mathcal R_B$ would give an index $i<N$ with
$$
\mathsf{Sep}_{S_B}(r_{i+1},T_B(r_i)).
$$
This contradicts state-separation soundness for the orbit-closure
witness supplied by $T_B$.
\end{proof}

\begin{corollary}[Layer-indexed materialization]
\label{cor:philosophy-layer-indexed-materialization}
If $B\triangleright_N A$, then $A$ has material appearance relative to
$B$ and lacks freedom-like appearance relative to $B$ over that prefix.
This does not imply $\neg\mathsf{FreeWill}(A)$, since
\autoref{def:philosophy-forbidden-absolute-freewill} supplies no such
context-free predicate.
\end{corollary}
\begin{proof}
The first assertion is the defining equivalence in
\autoref{def:philosophy-ledger-dominance}. The second follows from
\autoref{prop:philosophy-dominance-collapses-freedomlike}. The final
sentence records that only indexed judgments are available in this
schema.
\end{proof}

\begin{proposition}[Complexity is not dominance]
\label{prop:philosophy-complexity-not-dominance}
Greater ledger complexity for $B$ alone does not imply
$B\triangleright_N A$.
\end{proposition}
\begin{proof}
Ledger dominance requires the correct probe pattern, an identity
classifier adequate for $A$, a state classifier adequate for $A$'s
feedback, a rule $T_B\in\mathcal R_B$, and ledger witnesses for the
rule's success. A complexity comparison supplies none of these
certificate fields by itself.
\end{proof}

\begin{proposition}[Freedom-like appearance is stronger than randomness]
\label{prop:philosophy-freedomlike-stronger-than-randomness}
Freedom-like appearance implies identity closure. Hence randomness or
unpredictability alone is insufficient for freedom-like appearance.
\end{proposition}
\begin{proof}
By definition,
$$
\mathsf{FreedomLike}^N_{\mathcal O_A}(F_A)
\Longrightarrow
\mathsf{IdCl}^N_{\mathcal O_A}(F_A).
$$
Randomness may obstruct an orbit-closing rule, but without identity
closure the prefix is noise-like or unformed rather than freedom-like.
\end{proof}

\begin{definition}[Exposed prediction and reflexive escape]
\label{def:philosophy-exposed-prediction-reflexive-escape}
Let $T_A\in\mathcal R_A$ be a rule by which $A$ attempts to predict
the next response of $X$, and write $p=T_A(r_i)$. The prediction is
exposed to $X$ when $p$ becomes part of the feedback information
available to $X$ before the next response. The interface has reflexive
escape capacity at that stage when there is a response operation
$D_X$ with
$$
r_{i+1}=D_X(p)
\quad\text{and}\quad
\mathsf{Sep}_{S_A}(D_X(p),p).
$$
\end{definition}

\begin{proposition}[Exposed prediction obstructs complete orbit closure]
\label{prop:philosophy-exposed-prediction-obstructs-closure}
Assume state-separation soundness for $S_A$. If $p=T_A(r_i)$ is exposed
to $X$ and $X$ has reflexive escape capacity at stage $i$, then
$T_A$ does not orbit-close the prefix at that stage.
\end{proposition}
\begin{proof}
If $T_A$ orbit-closed the prefix, then
$$
S_A(r_{i+1},T_A(r_i)).
$$
Since $p=T_A(r_i)$ and $r_{i+1}=D_X(p)$, this gives
$S_A(D_X(p),p)$. Reflexive escape supplies
$\mathsf{Sep}_{S_A}(D_X(p),p)$, contradicting state-separation
soundness.
\end{proof}

\begin{corollary}[Hidden higher-layer prediction]
\label{cor:philosophy-hidden-higher-layer-prediction}
If a higher-layer prediction by $B$ is not visible to $A$, then the
specific diagonal obstruction in
\autoref{prop:philosophy-exposed-prediction-obstructs-closure} is not
available to $A$. A hidden, ledger-certified, state-sound rule may
therefore continue to materialize $A$ relative to $B$ over the given
prefix.
\end{corollary}
\begin{proof}
The diagonal obstruction requires exposure of the prediction to the
interface whose next response is being classified. Without that
exposure, the response operation using the prediction as input is not
part of the displayed feedback context.
\end{proof}

\begin{corollary}[De-indexing is the illicit promotion]
\label{cor:philosophy-deindexing-illicit-promotion}
The appearance itself is not the illicit step. The illicit step is the
promotion
$$
\mathsf{FreedomLike}^N_{\mathcal O_A}(F_A)
\quad\leadsto\quad
\mathsf{FreeWill}(X),
$$
which removes the observer, ledger, classifiers, rule family, and
prefix length.
\end{corollary}
\begin{proof}
The left-hand side is an admissible indexed judgment. The right-hand
side is the forbidden context-free predicate of
\autoref{def:philosophy-forbidden-absolute-freewill}.
\end{proof}

The resulting philosophical reading is neither an assertion that free
will absolutely exists nor a denial derived from a final global
observer. A stone lacks freedom-like appearance relative to an
observer who can identity-track it and close its fall under a
ledger-certified rule. Likewise, an observer-history $A$ lacks
freedom-like appearance relative to a stronger observer-history $B$
when $B$ can identity-track and orbit-close $A$'s feedback. These are
indexed materializations, not absolute eliminations. BEDC records
freedom-like appearance as real at the level of the finite ledger that
witnesses identity-preserving non-closure, and invalid only when that
indexed appearance is promoted into an observer-free substance claim.
