\chapter{A Concrete Naming Certificate for $\CompleteMetricLimitUniquenessUp$}
\label{ch:concrete-instances-complete-metric-limit-uniqueness-namecert}
\origin{human}

Following Bishop and Bridges on separated complete metric spaces, the $\CompleteMetricLimitUniquenessUp$ packet records the finite route by which two complete-metric limit rows for one displayed Cauchy source are compared through distance zero and then through the separated metric classifier. It sits over the complete-metric service of \autoref{ch:concrete-instances-completemetric-namecert}, the metric source of \autoref{ch:concrete-instances-metric-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the separated-limit uniqueness boundary of \autoref{ch:concrete-instances-separated-limit-uniqueness-namecert}. The packet names limit uniqueness only as displayed finite NameCert data; it does not identify quotient representatives, choose a limit, invoke countable choice, import ambient $\RealUp$ completeness, or export host point equality.

\begin{definition}[Complete metric limit uniqueness carrier]
\label{def:complete-metric-limit-uniqueness-carrier}
A $\CompleteMetricLimitUniquenessUp$ carrier is a finite $\BHist$ packet
$$
U=(A,L_{0},L_{1},M,Z,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the Cauchy-source row, exposing the finite request and tail data whose limit is being compared.
\item $L_{0}$ and $L_{1}$ are complete-metric limit rows for the same displayed source $A$.
\item $M$ is the $\MetricUp$ distance-witness row comparing the two displayed limit reads.
\item $Z$ is the $\RealUp$ zero-distance row reached from the distance witness through the regular rational readback surface.
\item $S$ is the separated-metric classifier row saying that the zero-distance read is the only admissible route from the two limit rows to a uniqueness handoff.
\item $H$ records componentwise $\hsame$ transport for the source, limit rows, distance witness, zero-distance row, separated classifier, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from the Cauchy-source request through the two limit rows, metric distance witness, Real zero-distance row, and separated classifier.
\item $P$ is the $\Pkg$ provenance over $\CompleteMetricLimitUniquenessUp$, $\CompleteMetricUp$, $\MetricUp$, $\RealUp$, $\RegSeqRatUp$, $\SeparatedMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompleteMetricLimitUniquenessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,L_{0},L_{1},M,Z,S,H,C,P,N$. It has no coordinate for quotient representatives, selected limits, countable choice, ambient $\RealUp$ completeness, or host equality of metric points.
\end{definition}

\begin{theorem}[Complete metric limit uniqueness NameCert obligations]
\label{thm:complete-metric-limit-uniqueness-namecert-obligations}
For every accepted $\CompleteMetricLimitUniquenessUp$ carrier
$$
U=(A,L_{0},L_{1},M,Z,S,H,C,P,N),
$$
the local $\NameCert_{\CompleteMetricLimitUniquenessUp}$ surface consists exactly of Cauchy-source admission for $A$, paired complete-metric limit admission for $L_{0}$ and $L_{1}$ over that source, metric distance-witness exactness for $M$, Real zero-distance readback for $Z$, separated classifier handoff for $S$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, sibling provenance through $P$, and local naming through $N$.

No complete-metric limit uniqueness obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source row $A$ is the only Cauchy datum available to the packet, and the two complete-metric rows $L_{0}$ and $L_{1}$ are admitted only as limit reads for that displayed source.

The comparison then passes through the metric witness $M$ and the Real zero-distance row $Z$. This records a finite distance-zero handoff, not a host equality of endpoints or an equality of quotient representatives.

Finally the separated classifier $S$ consumes that zero-distance row. The support rows $H,C,P,N$ transport, replay, source, and name the same route, so the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Complete metric limit uniqueness separatedness handoff]
\label{thm:complete-metric-limit-uniqueness-separatedness}
Every consumer that reads uniqueness from an accepted $\CompleteMetricLimitUniquenessUp$ carrier must factor the read through
$$
A,L_{0},L_{1},M,Z,S,H,C,P,N .
$$
The separatedness step is visible only after both complete-metric limit rows have been tied to the same Cauchy source, the $\MetricUp$ distance witness has been displayed, and the $\RealUp$ zero-distance row has been sealed. The handoff exports no quotient representative equality, selected limit, countable-choice schedule, ambient $\RealUp$ completeness principle, or host equality of metric points.
\end{theorem}
\begin{proof}
Start from an accepted carrier. The consumer first reads $A,L_{0},L_{1}$, so the two candidate limits are compared only as complete-metric limit rows for the same displayed Cauchy source.

The metric row $M$ then supplies the displayed distance comparison, and $Z$ seals the zero-distance read through the Real-facing route. At this point the carrier still has no coordinate for selected representatives or host point equality.

The separated classifier $S$ is the only row that turns the zero-distance evidence into a uniqueness handoff. Since $H,C,P,N$ merely preserve the same finite path, every accepted uniqueness read factors through the displayed rows and cannot escape into the excluded ambient principles.
\end{proof}

\closureat{CompleteMetricLimitUniquenessUp}{seedStr}

\begin{closurestatus}{\CompleteMetricLimitUniquenessUp}
  \constructivestory{A $\CompleteMetricLimitUniquenessUp$ packet is generated from one Cauchy-source row, two CompleteMetricUp limit rows, a MetricUp distance witness, a RealUp zero-distance row, a SeparatedMetricUp classifier handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-metric-limit-uniqueness-carrier}, \autoref{thm:complete-metric-limit-uniqueness-namecert-obligations}, and \autoref{thm:complete-metric-limit-uniqueness-separatedness} seed the finite complete-metric limit uniqueness packet over one Cauchy-source row, two complete-metric limit rows, a MetricUp distance witness, a RealUp zero-distance row, a separated classifier, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient representatives, selected limits, countable choice, ambient RealUp completeness, host point equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked Cauchy-source admission, paired complete-metric limit admission, distance-witness exactness, zero-distance sealing, separated classifier handoff, transport stability, replay stability, and non-escape for BEDC.Derived.CompleteMetricLimitUniquenessUp.}
\end{closurestatus}
