\chapter{A Concrete Naming Certificate for $\LegendreFenchelEnvelopeUp$}
\label{ch:concrete-instances-legendre-fenchel-envelope-namecert}
\origin{human}

Following Rockafellar, the $\LegendreFenchelEnvelopeUp$ packet names the finite convex-envelope surface obtained by reading epigraph windows, supporting affine minorants, convex-conjugate data, and biconjugate comparison rows before any optimization consumer may inspect the result. It sits after the convex-set carrier of \autoref{ch:concrete-instances-convexset-namecert}, the Fenchel-duality ledger of \autoref{ch:concrete-instances-fenchelduality-namecert}, and the proximal-resolvent handoff of \autoref{ch:concrete-instances-proximal-map-namecert}; it also exposes KKT-facing and convex-conjugate-facing rows for certificates that need a displayed envelope without importing an ambient lower-semicontinuous hull, host supremum operator, quotient function space, or choice-selected minimizer.

\begin{definition}[Legendre--Fenchel envelope carrier]
\label{def:legendre-fenchel-envelope}
A $\LegendreFenchelEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(W,A,D,B,R,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the epigraph window row, read through the $\ConvexSetUp$ carrier and recording the finite domain, value, and order comparisons visible to the envelope request.
\item $A$ is the supporting affine minorant ledger, listing the finitely displayed affine lower bounds and their compatibility with the same epigraph window.
\item $D$ is the convex conjugate readback row, exposing the pairing, dual-vector, and budgeted conjugacy data that a $\ConvexConjugateUp$ or $\FenchelDualityUp$ consumer may inspect.
\item $B$ is the biconjugate-envelope row, recording the displayed comparison between the primal epigraph window and the conjugate readback route.
\item $R$ is the proximal consumer row, allowing a $\ProximalMapUp$ request to read the envelope only after the window, minorant, conjugate, and biconjugate rows have been displayed.
\item $K$ is the KKT and Fenchel ledger row, tying stationarity, supporting minorants, and dual comparison data to the $\KKTUp$ and $\FenchelDualityUp$ packets.
\item $H$ records componentwise $\hsame$ transport for the epigraph window, affine minorants, conjugate readback, biconjugate envelope, proximal consumer, KKT and Fenchel ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from epigraph admission through supporting minorants, conjugate readback, biconjugate comparison, proximal consumption, and KKT/Fenchel ledger inspection.
\item $P$ is the $\Pkg$ provenance over $\LegendreFenchelEnvelopeUp$, $\ConvexSetUp$, $\ConvexConjugateUp$, $\FenchelDualityUp$, $\ProximalMapUp$, $\KKTUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LegendreFenchelEnvelopeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,A,D,B,R,K,H,C,P,N$. It has no coordinate for an external lower-semicontinuous hull, host biconjugation theorem, selected supremum witness, quotient equality of functions, ambient locally convex topology, or global minimization principle.
\end{definition}

\falsifiablePrediction{Every accepted $\LegendreFenchelEnvelopeUp$ consumer read factors through an epigraph window, supporting affine minorant ledger, convex conjugate readback, biconjugate-envelope row, proximal consumer row, KKT/Fenchel ledger row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert.}

\independenceWitness{convexset, fenchelduality, proximal-map, convex-conjugate, kkt: $\LegendreFenchelEnvelopeUp$ is not bijective to any listed sibling because it jointly carries an epigraph window, supporting affine minorants, conjugate readback, biconjugate envelope comparison, proximal consumer route, and KKT/Fenchel ledger in one finite packet.}

\closureat{LegendreFenchelEnvelopeUp}{seedStr}

\begin{closurestatus}{\LegendreFenchelEnvelopeUp}
  \constructivestory{A $\LegendreFenchelEnvelopeUp$ packet is generated from an epigraph window, supporting affine minorant ledger, convex conjugate readback, biconjugate-envelope row, proximal consumer row, KKT and Fenchel ledger row, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:legendre-fenchel-envelope} seeds the finite envelope certificate surface over convex-set, convex-conjugate, Fenchel-duality, proximal-map, and KKT rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a host biconjugation theorem, lower-semicontinuous hull existence, selected supporting functional, quotient function equality, ambient locally convex topology, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, affine-minorant ledger exactness, conjugate readback, biconjugate-envelope comparison, proximal consumer boundary, KKT/Fenchel ledger visibility, transport, replay, provenance, and local naming for BEDC.Derived.LegendreFenchelEnvelopeUp.}
\end{closurestatus}
