\chapter{A Concrete Naming Certificate for $\HausdorffUniformityCompletionUp$}
\label{ch:concrete-instances-hausdorff-uniformity-completion-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and Bourbaki on separated uniformities, the $\HausdorffUniformityCompletionUp$ packet records the completion neighbour where a uniformity source, a separated classifier, and a finite completion route are displayed in one NameCert surface. It sits after the uniform-space carrier of \autoref{ch:concrete-instances-uniformspace-namecert}, the Hausdorff-uniformity boundary of \autoref{ch:concrete-instances-hausdorff-uniformity-namecert}, the separated-reflection handoff of \autoref{ch:concrete-instances-separated-reflection-namecert}, the uniform-completion packet of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the metric-completion comparison surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the finite StreamName windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives L10 completion consumers a separated-uniform completion object without quotient equality, selected representatives, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[HausdorffUniformityCompletion carrier]
\label{def:hausdorff-uniformity-completion-carrier}
A $\HausdorffUniformityCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(U,H,S,C,M,W,R,E,T,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\UniformSpaceUp$ source row, including the finite entourage basis and refinement ledger read before any completion-facing request.
\item $H$ is the $\HausdorffUniformityUp$ separated-uniformity row, exposing the diagonal classifier for the same uniform source.
\item $S$ is the $\SeparatedReflectionUp$ row that routes indistinguishable Cauchy data through a displayed separated interface before a completion seal is consumed.
\item $C$ is the $\UniformCompletionUp$ row, recording the finite Cauchy-filter or Cauchy-net completion route served by $U,H,S$.
\item $M$ is the $\MetricCompletionUp$ comparison row used only when a metric-generated completion consumer asks for the same separated handoff.
\item $W$ is the $\StreamNameUp$ finite-window row through which completion observations are scheduled.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row obtained from the same displayed windows.
\item $E$ is the $\RealUp$ seal row, read only after $U,H,S,C,M,W,R$ have been displayed.
\item $T$ records componentwise $\hsame$ transport for the source, separated classifier, reflection, completion, comparison, window, readback, seal, replay, provenance, and local naming rows.
\item $Q$ records displayed $\Cont$ replay along the route from $U,H,S$ through $C,M,W,R,E$.
\item $P$ is the $\Pkg$ provenance over $\HausdorffUniformityCompletionUp$, $\UniformSpaceUp$, $\HausdorffUniformityUp$, $\SeparatedReflectionUp$, $\UniformCompletionUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HausdorffUniformityCompletionUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one separated-uniform completion packet. It contains no coordinate for quotient completion equality, selected Cauchy representatives, host point equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[HausdorffUniformityCompletion NameCert obligations]
\label{thm:hausdorff-uniformity-completion-namecert-obligations}
For every accepted $\HausdorffUniformityCompletionUp$ carrier
$$
K=(U,H,S,C,M,W,R,E,T,Q,P,N),
$$
the local $\NameCert_{\HausdorffUniformityCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed uniform-space source, Hausdorff-uniformity classifier, separated-reflection row, uniform-completion row, metric-completion comparison row, StreamName windows, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming rows;
\item uniform-source exactness, requiring every completion-facing request to begin with the finite entourage surface of $U$;
\item Hausdorff separation handoff, requiring indistinguishable Cauchy data to pass through $H$ and then through $S$ before the completion rows are visible;
\item completion readback stability, requiring $C,M,W,R,E$ to be consumed in the displayed order whenever a uniform or metric completion consumer asks for a separated endpoint read;
\item transport and replay stability through $T,Q$ for the same row order;
\item ledger non-escape, requiring $P$ and $N$ to name no quotient completion equality, selected representative, host equality, countable-choice schedule, open-cover compactness principle, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
No local obligation is stored outside these displayed rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:hausdorff-uniformity-completion-carrier}. The accepted tuple displays the uniform source, Hausdorff classifier, separated reflection, completion rows, finite windows, regular readback, real seal, and structural rows.

Uniform-source exactness follows from the first coordinate of the route. A completion-facing request must read $U$ before it can inspect the separated classifier or any completion row, so the request is tested against finite entourage data rather than an ambient host uniformity.

The separation handoff is the paired role of $H$ and $S$. The row $H$ records diagonal indistinguishability through the Hausdorff uniformity, and $S$ moves that evidence into the separated-reflection boundary before $C$ or $M$ can be consumed.

The completion readback is then confined to $C,M,W,R,E$. Transport and replay through $T,Q$ preserve the same order, while $P$ and $N$ package only the named rows. Hence none of the excluded quotient, representative-selection, choice, compactness, host-equality, or ambient-completeness readings can be projected as a NameCert obligation.
\end{proof}

\begin{theorem}[HausdorffUniformityCompletion separated handoff]
\label{thm:hausdorff-uniformity-completion-separated-handoff}
Every separated endpoint read exported by an accepted $\HausdorffUniformityCompletionUp$ carrier factors through the displayed route
$$
\UniformSpaceUp\longmapsto\HausdorffUniformityUp\longmapsto\SeparatedReflectionUp\longmapsto\UniformCompletionUp\longmapsto\MetricCompletionUp\longmapsto\StreamNameUp\longmapsto\RegSeqRatUp\longmapsto\RealUp .
$$
Consequently a completion consumer receives the separated-uniform completion surface only through finite entourage, reflection, completion, window, regular-readback, and seal rows; it receives no quotient completion equality, selected representative, countable-choice schedule, host equality, or ambient $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hausdorff-uniformity-completion-carrier}. The rows $U,H,S,C,M,W,R,E,T,Q,P,N$ are the only rows available to a separated completion consumer.

The route begins with $U$ and $H$, so the consumer first reads the displayed uniform source and the Hausdorff uniformity classifier. The separated-reflection row $S$ is the only handoff from indistinguishable Cauchy data to a separated completion boundary.

The completion rows $C$ and $M$ are downstream of that separated handoff. The finite-window row $W$, the regular readback row $R$, and the real seal row $E$ record the observable endpoint surface after the completion route has already been displayed.

Finally $T,Q,P,N$ transport, replay, package, and name the same finite route. Since no quotient equality, selected representative, choice schedule, host equality, or ambient completeness row occurs in the carrier, no separated endpoint read can export such a datum.
\end{proof}

\falsifiablePrediction{Every accepted $\HausdorffUniformityCompletionUp$ consumer reads $\UniformSpaceUp$, $\HausdorffUniformityUp$, $\SeparatedReflectionUp$, $\UniformCompletionUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ in the displayed route before citing separated completion uniqueness.}

\independenceWitness{uniformspace, hausdorff-uniformity, separated-reflection, uniformcompletion, metriccompletion, streamname, regseqrat, real: $\HausdorffUniformityCompletionUp$ is not bijective to any listed sibling because it jointly carries the uniform source, Hausdorff classifier, separated reflection, completion rows, finite windows, regular readback, real seal, transport, replay, provenance, and local NameCert row as one packet.}

\closureat{HausdorffUniformityCompletionUp}{seedStr}

\begin{closurestatus}{\HausdorffUniformityCompletionUp}
  \constructivestory{A $\HausdorffUniformityCompletionUp$ packet is generated from UniformSpace, HausdorffUniformity, SeparatedReflection, UniformCompletion, MetricCompletion, StreamName, RegSeqRat, Real, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-uniformity-completion-carrier}, \autoref{thm:hausdorff-uniformity-completion-namecert-obligations}, and \autoref{thm:hausdorff-uniformity-completion-separated-handoff} seed the separated-uniform completion boundary over displayed uniformity, reflection, completion, finite-window, regular-readback, real-seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, quotient completion equality, selected representatives, countable choice, host equality, open-cover compactness, bridge checking, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform-source exactness, Hausdorff separation handoff, completion readback stability, transport and replay stability, and ledger non-escape for BEDC.Derived.HausdorffUniformityCompletionUp.}
\end{closurestatus}
