\begin{theorem}[RegSeqRat constant stream spine]
\label{thm:regseqrat-constant-stream-spine}
For every history $d:\Hist$, a carrier
$\mathsf{RatHistoryCarrier}(d)$ supplies a $\RegSeqRat$ stream certificate spine
for $\mathsf{RatConstStream}_d$. The spine consists of the
$\mathsf{RatStreamNameCarrier}(\mathsf{RatConstStream}_d)$ row, the self
$\mathsf{RealUnaryStreamClassifier}(\mathsf{RatConstStream}_d,
\mathsf{RatConstStream}_d)$ row, and a constant regularity ledger: at any two
certified unary observation indices, both exposed endpoints are the same
$\RatUp$ point $d$, and every dyadic-tolerance request is discharged by RatUp
classifier reflexivity.
\end{theorem}
\begin{proof}
Apply the carrier half of
\autoref{thm:rat-stream-name-constant-point-exactness} from right to left to
the displayed $\mathsf{RatHistoryCarrier}(d)$. This gives the stream-name
carrier row for $\mathsf{RatConstStream}_d$.

For the classifier row, unfold
Definition~\ref{def:real-unary-observation-stream-classifier}. A certified
unary observation $n$ reads
$\mathsf{RatConstStream}_d(n)=d$, so the required pointwise
$\mathsf{RatHistoryClassifier}(\mathsf{RatConstStream}_d(n),
\mathsf{RatConstStream}_d(n))$ is RatUp classifier reflexivity at the supplied
carrier of $d$.

The regularity ledger is constant. Given any two certified unary observation
indices, the point-exactness theorem identifies both exposed endpoints with
the same RatUp point $d$. Thus the two observations have the same carrier, and
each dyadic tolerance request compares $d$ with itself, again by RatUp
reflexivity. These rows are exactly the data named in
Definition~\ref{def:regseqrat-stream-certificate-spine}.
\end{proof}

\begin{theorem}[RegSeqRat reindexed constant stream spine]
\label{thm:regseqrat-reindexed-constant-stream-spine}
For histories $d,e:\Hist$ and observation schedules $r,q:\Hist\to\Hist$,
$\mathsf{RatHistoryCarrier}(d)$ supplies $\RegSeqRat$ stream certificate
spines for both $\mathsf{RatConstStream}_d\circ r$ and
$\mathsf{RatConstStream}_d$. If $\mathsf{RatHistoryClassifier}(d,e)$ is
supplied, then the two independently reindexed constant streams
$\mathsf{RatConstStream}_d\circ r$ and
$\mathsf{RatConstStream}_e\circ q$ carry compatible $\RegSeqRat$ stream
certificate spines and the classifier row
$\mathsf{RealUnaryStreamClassifier}(\mathsf{RatConstStream}_d\circ r,
\mathsf{RatConstStream}_e\circ q)$.
\end{theorem}
\begin{proof}
First build the carried stream rows. Apply
\autoref{thm:rat-stream-name-independent-reindexed-constant-classifier} to the
carrier row of $d$ to obtain the stream-name carrier for
$\mathsf{RatConstStream}_d\circ r$, and apply
\autoref{thm:regseqrat-constant-stream-spine} to the same carrier row to obtain
the unreindexed constant-stream spine.

The regularity ledger for $\mathsf{RatConstStream}_d\circ r$ is the same
constant ledger used in \autoref{thm:regseqrat-constant-stream-spine}. At any
certified unary observation index, the schedule $r$ is read before the constant
stream is evaluated, and the exposed endpoint is still $d$. Thus every dyadic
tolerance request again compares the RatUp point $d$ with itself and is
discharged by RatUp classifier reflexivity.

Now suppose $\mathsf{RatHistoryClassifier}(d,e)$ is supplied. Its endpoint
carrier rows provide the corresponding constant regularity ledgers for the
$d$-stream and the $e$-stream. The StreamNameUp classifier row follows from
\autoref{thm:rat-stream-name-independent-reindexed-constant-classifier}, while
\autoref{thm:real-constant-independent-reindexed-stream-bridge} reads the same
point classifier as the RealUp unary-observation stream classifier for the two
independently reindexed constant streams.

Combining these rows gives the two compatible $\RegSeqRat$ spines together with
the displayed $\mathsf{RealUnaryStreamClassifier}$ row. No quotient,
completion, or host real structure is used.
\end{proof}

\begin{theorem}[RegSeqRat constant stream seal classifier package]
\label{thm:regseqrat-constant-stream-seal-classifier-package}
Let $X$ and $Y$ be sealed $\RealUp$ candidates exposing
$\mathsf{RatConstStream}_d\circ r$ and
$\mathsf{RatConstStream}_e\circ q$, respectively. If the two exposed streams
carry the compatible $\RegSeqRat$ stream certificate spines supplied by
\autoref{thm:regseqrat-reindexed-constant-stream-spine}, and if the seal
records the displayed row
$\mathsf{RealUnaryStreamClassifier}(\mathsf{RatConstStream}_d\circ r,
\mathsf{RatConstStream}_e\circ q)$, then the seal exports the RealUp
observation classifier required by
\autoref{def:real-classifier-specification}.
\end{theorem}
\begin{proof}
Project the two exposed rational-observation streams from the $\RealUp$ seals.
By hypothesis, the two streams already carry the $\RegSeqRat$ spines produced
for the independently reindexed constant streams.

Use the classifier row supplied by
\autoref{thm:regseqrat-reindexed-constant-stream-spine}. It is exactly the
$\mathsf{RealUnaryStreamClassifier}(\mathsf{RatConstStream}_d\circ r,
\mathsf{RatConstStream}_e\circ q)$ row recorded by the seal.

Finally apply \autoref{thm:regseqrat-realup-seal-consumes-stream-spine} to the
two spines and the displayed stream classifier. The conclusion is precisely
the RealUp observation classifier named in
\autoref{def:real-classifier-specification}.
\end{proof}
