\begin{theorem}[RegSeqRat carrier obligation]
\label{thm:regseqrat-carrier-obligation}
The carrier obligation for $\RegSeqRat$ is exactly the
$\mathsf{RatStreamNameCarrier}$ row together with the regularity witness over
$\mathsf{UnaryHistory}$ observations. Concretely, for a rational-observation
map $s:\Hist\to\Hist$, a $\RegSeqRat$ carrier consists of
$\mathsf{RatStreamNameCarrier}(s)$ and a ledger which, at each certified unary
observation index $n$, exposes the endpoint $\RatUp$ carrier row
$\mathsf{RatHistoryCarrier}(s(n))$ and the dyadic-tolerance witness demanded by
the stream regularity check.
\end{theorem}
\begin{proof}
Unfold the spine named in
Definition~\ref{def:regseqrat-stream-certificate-spine}. Its first component
is the $\mathsf{RatStreamNameCarrier}$ row, and its ledger is indexed only by
certified $\mathsf{UnaryHistory}$ observations.

The endpoint carrier rows are supplied by
\autoref{thm:regseqrat-stream-classifier-stability-spine}; the constant case is
supplied by \autoref{thm:regseqrat-constant-stream-spine}. The public package
\autoref{thm:regseqrat-stream-spine-scoped-package} records these rows as the
carrier face of the scoped spine.

The seal consumer
\autoref{thm:regseqrat-realup-seal-consumes-stream-spine} uses no carrier data
outside this spine. Thus the carrier obligation is precisely the named
stream-name carrier plus the unary-observation regularity ledger.
\end{proof}

\begin{theorem}[RegSeqRat classifier obligation]
\label{thm:regseqrat-classifier-obligation}
The classifier obligation for $\RegSeqRat$ is exactly
$\mathsf{RealUnaryStreamClassifier}$ read with
$\mathsf{RatStreamNameClassifier}$ endpoint recovery. For carried streams
$s,t:\Hist\to\Hist$, a classifier row records the pointwise $\RatUp$
comparison over every certified $\mathsf{UnaryHistory}$ observation and
recovers the two endpoint stream-name carrier rows used by
$\mathsf{RatStreamNameClassifier}(s,t)$.
\end{theorem}
\begin{proof}
Start from Definition~\ref{def:regseqrat-stream-certificate-spine}. The spine
does not introduce a separate classifier relation; it stores the RealUp unary
stream classifier over the same BEDC unary observations.

Apply \autoref{thm:regseqrat-stream-classifier-stability-spine}. It reads the
pointwise $\RatUp$ classifier rows from
$\mathsf{RealUnaryStreamClassifier}$, recovers the endpoint carrier rows, and
repackages the transported data as a
$\mathsf{RatStreamNameClassifier}$ row. The constant boundary is the reflexive
case supplied by \autoref{thm:regseqrat-constant-stream-spine}.

The scoped package
\autoref{thm:regseqrat-stream-spine-scoped-package} lists the reflexive,
symmetric, transitive, and transported classifier rows together. The seal
consumer \autoref{thm:regseqrat-realup-seal-consumes-stream-spine} confirms
that the same row is the classifier exported through the $\RealUp$ interface.
\end{proof}

\begin{definition}[DyadicRatCore observation row]
\label{def:dyadic-rat-core-observation-row}
A DyadicRatCore observation row for a BEDC history $d$ is the package consisting
of a $\mathsf{RatHistoryCarrier}(d)$ witness, a positive unary denominator row
$\mathsf{PositiveUnaryDenominator}(d)$, and the dyadic-radius token used by the
$\RegSeqRat$ regularity check. Its classifier face is inherited from
$\mathsf{RatHistoryClassifier}$, together with $\hsame$ transport of the
positive-denominator row.
\end{definition}

\begin{theorem}[DyadicRatCore observation-row classifier transport]
\label{thm:dyadic-rat-core-observation-row-classifier-transport}
Let $d,e,d',e':\Hist$. Suppose $d$ and $e$ carry
$\mathsf{DyadicRatCoreObservationRow}$ packages, suppose
$\mathsf{RatHistoryClassifier}(d,e)$ holds, and suppose
$\hsame(d,d')$ and $\hsame(e,e')$ hold. If the dyadic-radius tokens for
$d'$ and $e'$ are the same certified unary-observation requests as the
tokens for $d$ and $e$, transported along those two $\hsame$ rows inside the
$\RegSeqRat$ ledger, then $d'$ and $e'$ carry
$\mathsf{DyadicRatCoreObservationRow}$ packages and
$\mathsf{RatHistoryClassifier}(d',e')$ holds.
\end{theorem}
\begin{proof}
Unpack Definition~\ref{def:dyadic-rat-core-observation-row}. The source rows
at $d$ and $e$ consist of rational-history carriers, positive unary
denominator rows, and dyadic-radius tokens attached to certified
$\RegSeqRat$ unary observations.

Apply the RatUp classifier transport to
$\mathsf{RatHistoryClassifier}(d,e)$ along $\hsame(d,d')$ and
$\hsame(e,e')$. This gives the transported classifier
$\mathsf{RatHistoryClassifier}(d',e')$, and the transported carrier rows are
read from the same rational-history endpoint spine.

The denominator component follows by positive-denominator transport. Applying
\autoref{thm:rat-positive-unary-denominator-hsame-transport} to the two
$\hsame$ rows carries the positive unary denominator rows from $d$ to $d'$
and from $e$ to $e'$.

Finally, the dyadic-radius component is ledger-attached to the same certified
unary-observation requests in the $\RegSeqRat$ spine. Transporting the
endpoint rows changes neither the request names nor the recorded
dyadic-tolerance tokens, so no completion or quotient datum is introduced.
Repacking the transported carrier, denominator, token, and classifier rows
gives the stated DyadicRatCore observation-row transport.
\end{proof}

The fit is as follows: traditional target dyadic rational observation
transport; BEDC source RatUp plus RegSeqRat unary requests over
$\mathsf{BHist}$; carrier $\mathsf{DyadicRatCoreObservationRow}$; classifier
$\mathsf{RatHistoryClassifier}$; stability transported denominator rows;
ledger unchanged dyadic-radius request; core theorem
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport};
exactness transported row plus classifier; standard bridge finite RealUp
windows; status $\mathsf{ProofTarget}$.

\begin{theorem}[DyadicRatCore scoped source package]
\label{thm:dyadic-rat-core-scoped-source-package}
The DyadicRatCore source used by $\RegSeqRat$ is the concrete BEDC scoped
source package over $\Hist$ whose carrier, classifier, stability, and ledger
faces are all read from the rational-history endpoint spine. For each endpoint
history $d$, the carrier face is
$\mathsf{RatHistoryCarrier}(d)$ together with
$\mathsf{PositiveUnaryDenominator}(d)$ and the dyadic-radius token recorded by
the $\RegSeqRat$ regularity request. For endpoints $d,e$, the classifier face
is $\mathsf{RatHistoryClassifier}(d,e)$ together with $\hsame$ transport of the
positive-denominator rows. The stability face is inherited from the $\RatUp$
carrier and classifier transports and from the pointwise classifier obligation
of $\RegSeqRat$. The ledger face is exactly the finite family of
dyadic-tolerance requests already recorded in the $\RegSeqRat$ spine.
\end{theorem}
\begin{proof}
Start with the carrier face. Definition~\ref{def:dyadic-rat-core-observation-row}
names the three endpoint rows: the rational-history carrier, the positive
unary denominator, and the dyadic-radius token. The endpoint carrier and the
finite dyadic request are supplied by
\autoref{thm:regseqrat-carrier-obligation}, while
\autoref{thm:rat-history-carrier-positive-denominator-equivalence} converts
the carrier row into the positive-denominator row.

Next read the classifier and stability faces. The pointwise stream classifier
obligation in \autoref{thm:regseqrat-classifier-obligation} exposes the
$\mathsf{RatHistoryClassifier}(d,e)$ endpoint comparison used by the
DyadicRatCore source. RatUp carrier and classifier transport carries the
rational-history rows along the same $\hsame$ comparison, and
\autoref{thm:rat-positive-unary-denominator-hsame-transport} carries the
positive-denominator row.

It remains only to identify the ledger. No request outside the
$\RegSeqRat$ spine is used: the dyadic-radius token is attached to the same
certified unary observation entry that supplies the endpoint rational row.
Thus the source package has precisely the stated carrier, classifier,
stability, and finite ledger faces over $\Hist$.
\end{proof}

\begin{theorem}[DyadicRatCore observation row hsame transport]
\label{thm:dyadic-rat-core-observation-row-hsame-transport}
Let $d,e:\Hist$. If $d$ has a DyadicRatCore observation row in the sense of
\autoref{def:dyadic-rat-core-observation-row} and $\hsame(d,e)$ holds, then
$e$ has a DyadicRatCore observation row. Its $\mathsf{RatHistoryCarrier}(e)$
component is the $\RatUp$ carrier transport of the carrier component at $d$,
its $\mathsf{PositiveUnaryDenominator}(e)$ component is transported by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}, and its
dyadic-radius token is the same certified observation ledger entry of the
$\RegSeqRat$ spine.
\end{theorem}
\begin{proof}
Unpack the row named by
\autoref{def:dyadic-rat-core-observation-row}. It consists of a
$\mathsf{RatHistoryCarrier}(d)$ row, a
$\mathsf{PositiveUnaryDenominator}(d)$ row, and a dyadic-radius token attached
to a certified unary observation entry in the $\RegSeqRat$ regularity ledger.

Transport the carrier face along $\hsame(d,e)$ using the $\RatUp$ carrier
transport already used in
\autoref{thm:dyadic-rat-core-scoped-source-package}. The compatibility between
the rational-history carrier and the positive-denominator row is the one
identified by
\autoref{thm:rat-history-carrier-positive-denominator-equivalence}.

Now apply
\autoref{thm:rat-positive-unary-denominator-hsame-transport} to carry the
positive-denominator component from $d$ to $e$. The endpoint rational row and
the certified dyadic request are the rows recorded by
\autoref{thm:regseqrat-carrier-obligation} inside the scoped spine of
\autoref{thm:regseqrat-stream-spine-scoped-package}.

The dyadic-radius token is not recomputed during transport: it remains attached
to the same certified observation ledger entry used by the source package.
Thus the transported carrier row, the transported positive-denominator row,
and the unchanged ledger token repack as a DyadicRatCore observation row for
$e$.
\end{proof}

The intended Lean target shape for this boundary is
\texttt{BEDC.Derived.RealUp.DyadicRatCore\_scoped\_source\_package}.

\begin{theorem}[DyadicRatCore carrier and classifier obligations]
\label{thm:dyadic-rat-core-carrier-classifier-obligations}
The carrier and classifier obligations for DyadicRatCore are the certificate
boundary whose carrier row is
$\mathsf{DyadicRatCoreObservationRow}(d)$ from
\autoref{def:dyadic-rat-core-observation-row}, whose classifier row is
$\mathsf{RatHistoryClassifier}(d,e)$ transported through
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}, and whose
source package is the scoped boundary of
\autoref{thm:dyadic-rat-core-scoped-source-package}. Concretely, for each
endpoint history $d:\Hist$, the carrier obligation reads exactly the
$\mathsf{RatHistoryCarrier}(d)$ row, the
$\mathsf{PositiveUnaryDenominator}(d)$ row, and the dyadic-radius token already
recorded by the $\RegSeqRat$ ledger. For each classifier comparison
$\mathsf{RatHistoryClassifier}(d,e)$, the classifier obligation transports
that three-field row along $\hsame(d,e)$ and repacks no additional completion,
quotient, or external metric datum.
\end{theorem}
\begin{proof}
Unpack the definition of the observation row. The carrier face is precisely the
triple named in \autoref{def:dyadic-rat-core-observation-row}: a RatUp endpoint
carrier, a positive unary denominator row, and the dyadic-radius token from the
regularity ledger.

Now use \autoref{thm:dyadic-rat-core-scoped-source-package}. It identifies the
source of every such row as the RatUp endpoint history together with the
$\RegSeqRat$ observation request, so the carrier obligation has no independent
object outside that scoped package.

For the classifier face, apply
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}. The
$\mathsf{RatHistoryClassifier}$ comparison supplies the $\hsame$ transport of
the endpoint carrier, denominator row, and dyadic token, which is exactly the
DyadicRatCore classifier obligation.
\end{proof}

\begin{theorem}[DyadicRatCore arithmetic-stability obligations]
\label{thm:dyadic-rat-core-arithmetic-stability-obligations}
The arithmetic-stability obligations for DyadicRatCore are the finite
certificate rows required to read dyadic rational endpoint arithmetic through
the BEDC source package. They consist of operation rows for dyadic addition,
negation, subtraction, multiplication, and positive-denominator division;
classifier congruence rows showing that $\mathsf{RatHistoryClassifier}$ and
$\hsame$ transport carry equivalent inputs to equivalent operation outputs;
denominator-preservation rows showing that the
$\mathsf{PositiveUnaryDenominator}$ face remains in the DyadicRatCore carrier
after each operation; and finite ledger provenance rows tying every requested
operation to the dyadic observation ledger consumed by the $\RegSeqRat$
regularity check. These are obligations for formal proof targets over the
existing RatUp, StreamNameUp, $\mathsf{BHist}$, $\hsame$, and dyadic ledger
interfaces; they do not assert arithmetic laws beyond that certificate
inventory.
\end{theorem}
\begin{proof}
Read every operation input as a DyadicRatCore observation row using
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. This exposes the
RatUp carrier, the positive denominator row, and the dyadic-radius token at
each endpoint.

The operation row is then a finite BEDC request over the same endpoint
histories. RatUp supplies the rational endpoint operation, StreamNameUp keeps
the requested stream observation name stable, and the dyadic ledger records the
finite observation request consumed downstream by $\RegSeqRat$.

Classifier congruence is the same transport pattern used for the carrier and
classifier boundary. The $\mathsf{RatHistoryClassifier}$ comparison and
$\hsame$ denominator transport carry equivalent inputs to the corresponding
operation outputs, while denominator preservation keeps the result inside the
DyadicRatCore observation-row format.
\end{proof}

\begin{theorem}[DyadicRatCore radius, distance, and absolute-value obligations]
\label{thm:dyadic-rat-core-radius-distance-obligations}
The monotone dyadic-radius, distance, and absolute-value obligations for
DyadicRatCore are the certificate rows consumed by $\RegSeqRat$ regularity and
by the $\RealUp$ sealing boundary. The radius obligation states that
strengthening a finite dyadic-radius request preserves the same RatUp endpoint
carrier and transports only the ledger token. The distance obligation states
that dyadic endpoint distance is read from two
$\mathsf{DyadicRatCoreObservationRow}$ inputs, is stable under
$\mathsf{RatHistoryClassifier}$ and $\hsame$ transport, and records its output
in the same finite ledger. The absolute-value obligation is the unary instance
of the same pattern: it reads one endpoint row, preserves positive-denominator
and classifier compatibility, and exposes the output row required by the
$\RegSeqRat$ regularity spine before $\RealUp$ sealing.
\end{theorem}
\begin{proof}
Begin with the carrier and classifier package of
\autoref{thm:dyadic-rat-core-carrier-classifier-obligations}. It gives the
endpoint rows and their $\mathsf{RatHistoryClassifier}$ transport inside
$\mathsf{BHist}$ and $\hsame$.

For radius monotonicity, refine the finite dyadic request in the ledger. The
RatUp endpoint carrier and the positive-denominator face remain fixed, while
the dyadic-radius token is replaced by the stronger certified request used by
the $\RegSeqRat$ regularity spine.

For distance and absolute value, use the same operation-row shape as in
\autoref{thm:dyadic-rat-core-arithmetic-stability-obligations}. The binary
distance row and the unary absolute-value row read only DyadicRatCore carrier
data, preserve classifier compatibility under $\hsame$, and expose exactly the
finite output rows consumed by the RealUp sealing interface.
\end{proof}

\begin{closurestatus}{\DyadicRatCore}
  \theoryclosure{\obligationClosure}
  \scopeclosed{The obligation scope is the DyadicRatCore carrier and classifier row, dyadic arithmetic-stability inventory, monotone dyadic-radius inventory, distance and absolute-value stability inventory, RatUp endpoint histories, StreamNameUp request names, $\mathsf{BHist}$, $\hsame$, and the finite dyadic ledger consumed by RegSeqRat and RealUp.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.RealUp.DyadicRatCore\_scoped\_source\_package}
  \bridgestatus{none}
  \notclaimed{This block does not claim $\scopedClosure$, $\RegSeqRat$ or $\RealUp$ completion, $\RealUp$ arithmetic or order, metric completeness, or a standard bridge.}
  \upgradepath{$\scopedClosure$ requires each obligation proof to bind its exact BEDC primitives and Lean-side targets without treating paper closure as machine verification.}
\end{closurestatus}

\begin{theorem}[DyadicRatCore distance obligation]
\label{thm:dyadic-rat-core-distance-obligation}
For endpoints $d,e:\Hist$, the DyadicRatCore distance obligation is the finite
certificate package consisting of two
$\mathsf{DyadicRatCoreObservationRow}$ witnesses, the displayed
$\mathsf{RatHistoryClassifier}(d,e)$ face, the positive-denominator transports
for both endpoints, and the dyadic-radius ledger token used by the $\RegSeqRat$
regularity request. Under $\hsame$ transport of both endpoints, the same
package transports endpointwise to the corresponding target endpoints.
\end{theorem}
\begin{proof}
Unpack \autoref{def:dyadic-rat-core-observation-row}. Each endpoint row gives
the rational-history carrier, the positive unary denominator, and the
dyadic-radius token attached to a certified unary observation ledger entry.

The finite source of these rows is the scoped package of
\autoref{thm:dyadic-rat-core-scoped-source-package}. Its classifier face is the
displayed $\mathsf{RatHistoryClassifier}(d,e)$ row, and its endpoint rows are
exactly the two observation-row witnesses used by the distance request.

Transport the classifier face with
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}. Transport
each endpoint row with
\autoref{thm:dyadic-rat-core-observation-row-hsame-transport}; the
positive-denominator components are carried endpointwise by the same rows.

The dyadic-radius ledger token remains the certified token already recorded by
the $\RegSeqRat$ regularity request. Thus the transported endpoint rows,
transported classifier face, positive-denominator transports, and unchanged
ledger token repack as the transported distance-obligation package, with no
quotient or completion datum read.
\end{proof}

\begin{theorem}[DyadicRatCore absolute-value obligation]
\label{thm:dyadic-rat-core-absolute-value-obligation}
For an endpoint $d:\Hist$, the DyadicRatCore absolute-value obligation is the
unary-radius face obtained from a single
$\mathsf{DyadicRatCoreObservationRow}(d)$. It preserves the
$\mathsf{PositiveUnaryDenominator}(d)$ component, records the same
dyadic-radius request, and is stable under the $\hsame$ transport supplied by
the scoped source package.
\end{theorem}
\begin{proof}
Project the carrier, positive-denominator, and dyadic-radius components from
\autoref{def:dyadic-rat-core-observation-row}. These three projections are the
unary-radius face consumed by the absolute-value request.

The positive-denominator component transports along
\autoref{thm:rat-positive-unary-denominator-hsame-transport}. The whole
observation row transports along
\autoref{thm:dyadic-rat-core-observation-row-hsame-transport}, so the carrier
and dyadic-radius components remain aligned with the transported endpoint.

Repack the transported row as the absolute-value obligation face. The scoped
source package of \autoref{thm:dyadic-rat-core-scoped-source-package} supplies
the $\hsame$ transport used here, and no additional arithmetic, quotient, or
completion datum is introduced.
\end{proof}

\begin{theorem}[DyadicRatCore carrier obligation]
\label{thm:dyadic-rat-core-carrier-obligation}
The carrier obligation for DyadicRatCore is the ten-field certificate boundary
whose traditional target is dyadic rational endpoint observation; whose BEDC
source is $\RatUp$ endpoint histories together with
$\mathsf{PositiveUnaryDenominator}$ and the $\RegSeqRat$ dyadic-radius token;
whose carrier is the DyadicRatCore observation row of
\autoref{def:dyadic-rat-core-observation-row}; whose classifier is
$\mathsf{RatHistoryClassifier}$ together with $\hsame$ transport of the
denominator row; whose stability face is inherited from the $\RatUp$ endpoint
carrier laws and the $\RegSeqRat$ carrier obligation; whose ledger is the
finite dyadic-tolerance request already recorded in the stream spine; whose
core theorem is the scoped source package of
\autoref{thm:dyadic-rat-core-scoped-source-package}; whose exactness clause
states that no carrier datum outside the observation row is read; whose
standard bridge is the finite RealUp observation window; and whose status is
$\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Unpack the scoped source package in
\autoref{thm:dyadic-rat-core-scoped-source-package}. Its endpoint source is
exactly a $\RatUp$ history observation equipped with the positive unary
denominator row and the dyadic-radius token from the certified
$\RegSeqRat$ request.

Apply \autoref{thm:regseqrat-carrier-obligation}. It supplies the endpoint
$\mathsf{RatHistoryCarrier}$ row and the finite dyadic-tolerance ledger entry.
The denominator component is the RatUp positive-denominator transport face
already used by the scoped source package.

The FKernel and $\Cont$ unary context laws keep the request name and its
finite ledger position fixed while the endpoint history is read. Thus the
carrier face is precisely the existing DyadicRatCore observation row, with no
extra completion or quotient object.
\end{proof}

\begin{theorem}[DyadicRatCore classifier obligation]
\label{thm:dyadic-rat-core-classifier-obligation}
The classifier obligation for DyadicRatCore is the ten-field certificate
boundary whose traditional target is dyadic endpoint comparison; whose BEDC
source is the pair of $\RatUp$ endpoint histories read from certified
$\RegSeqRat$ unary observations; whose carrier is the pair of DyadicRatCore
observation rows; whose classifier is $\mathsf{RatHistoryClassifier}$ plus
$\hsame$ transport of $\mathsf{PositiveUnaryDenominator}$; whose stability face
is the endpointwise classifier transport of $\RegSeqRat$; whose ledger is the
same finite dyadic-tolerance request on both endpoints; whose core theorem is
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport}; whose
exactness clause says that the transported row is repacked from the same
carrier, denominator, and token fields; whose standard bridge is the finite
RealUp comparison window; and whose status is $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Start from the classifier face named in
\autoref{thm:dyadic-rat-core-scoped-source-package}. The only comparison row
there is $\mathsf{RatHistoryClassifier}$ on the endpoint histories.

Apply \autoref{thm:regseqrat-classifier-obligation}. It recovers the
pointwise endpoint comparison from the stream classifier and supplies the
same certified unary observation positions on the two streams.

Positive-denominator transport carries the denominator rows along the
$\hsame$ comparisons, and the FKernel unary context laws keep the finite
dyadic request attached to the same observation name. Therefore
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport} repacks
the transported endpoint data as the stated classifier obligation.
\end{proof}

\begin{theorem}[DyadicRatCore arithmetic-stability obligation]
\label{thm:dyadic-rat-core-arithmetic-stability-obligation}
The arithmetic-stability obligation for DyadicRatCore is the ten-field
certificate boundary whose traditional target is closure of dyadic endpoint
arithmetic under the rational endpoint interface; whose BEDC source is the
$\RatUp$ endpoint histories carrying
$\mathsf{PositiveUnaryDenominator}$ rows and the $\RegSeqRat$
dyadic-radius token; whose carrier is the DyadicRatCore observation row for
each arithmetic input and output endpoint; whose classifier is
$\mathsf{RatHistoryClassifier}$ transported along $\hsame$; whose stability
face is the RatUp arithmetic context read through FKernel and $\Cont$ unary
laws; whose ledger is the finite dyadic-tolerance request used by the stream
regularity check; whose core theorem is
\autoref{thm:dyadic-rat-core-scoped-source-package}; whose exactness clause
says that arithmetic stability uses only endpoint carrier rows, denominator
transport, and the dyadic token; whose standard bridge is the finite RealUp
arithmetic observation window; and whose status is $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Read the arithmetic inputs through
\autoref{thm:dyadic-rat-core-carrier-obligation}. Each input endpoint exposes
a rational-history carrier, a positive unary denominator row, and the
dyadic-radius ledger token.

The RatUp arithmetic context supplies the endpoint rational operation inside
the FKernel unary context. The $\Cont$ laws keep the requested unary
observation name stable, so the output endpoint is recorded in the same
finite dyadic-tolerance ledger format used by
\autoref{thm:regseqrat-carrier-obligation}.

Classifier compatibility is supplied by
\autoref{thm:dyadic-rat-core-classifier-obligation}. Its
$\mathsf{RatHistoryClassifier}$ row and positive-denominator transport ensure
that replacing any input by an $\hsame$ endpoint replaces the output by the
corresponding transported DyadicRatCore row.
\end{proof}

\begin{theorem}[DyadicRatCore monotone-radius obligation]
\label{thm:dyadic-rat-core-monotone-radius-obligation}
The monotone-radius obligation for DyadicRatCore is the ten-field certificate
boundary whose traditional target is preservation of certified dyadic
tolerance when a requested unary radius is made stronger; whose BEDC source is
the $\RatUp$ endpoint history, the
$\mathsf{PositiveUnaryDenominator}$ row, and the $\RegSeqRat$ dyadic-radius
token; whose carrier is the DyadicRatCore observation row at the endpoint;
whose classifier is $\mathsf{RatHistoryClassifier}$ with $\hsame$ denominator
transport; whose stability face is the FKernel monotonicity of finite unary
requests inside the $\Cont$ context; whose ledger is the finite
dyadic-tolerance request ordered by the unary observation radius; whose core
theorem is \autoref{thm:dyadic-rat-core-scoped-source-package}; whose
exactness clause says that strengthening the radius refines only the ledger
token and not the endpoint carrier; whose standard bridge is the finite
RealUp observation window; and whose status is $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Begin with the endpoint row supplied by
\autoref{thm:dyadic-rat-core-carrier-obligation}. Its dyadic-radius token is a
finite ledger entry of the $\RegSeqRat$ regularity spine, not an independent
metric object.

Apply the FKernel finite-request monotonicity inside the $\Cont$ unary
context. A stronger unary radius refines the same certified observation
request and therefore preserves the endpoint $\RatUp$ carrier and the
positive-denominator row.

The classifier side is unchanged by the refinement. If the endpoint is moved
along $\hsame$, \autoref{thm:dyadic-rat-core-classifier-obligation} transports
the carrier and denominator fields, while the refined dyadic token remains in
the same finite ledger family.
\end{proof}

\begin{theorem}[DyadicRatCore distance and absolute-value obligation]
\label{thm:dyadic-rat-core-distance-absolute-obligation}
The distance and absolute-value obligation for DyadicRatCore is the ten-field
certificate boundary whose traditional target is endpoint stability of
dyadic distance and absolute value; whose BEDC source is the pair of $\RatUp$
endpoint histories with $\mathsf{PositiveUnaryDenominator}$ rows and the
$\RegSeqRat$ dyadic-radius token; whose carrier is the DyadicRatCore
observation row for each endpoint and for the distance or absolute-value
output; whose classifier is $\mathsf{RatHistoryClassifier}$ transported by
$\hsame$ with denominator transport; whose stability face is the RatUp unary
context law for distance and absolute value inside FKernel and $\Cont$; whose
ledger is the finite dyadic-tolerance request; whose core theorem is
\autoref{thm:dyadic-rat-core-scoped-source-package}; whose exactness clause
says that distance and absolute value read only the carrier row, classifier
row, denominator transport, and dyadic token; whose standard bridge is the
finite RealUp metric observation window; and whose status is
$\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Use \autoref{thm:dyadic-rat-core-carrier-obligation} to expose the endpoint
rows for the inputs. The RatUp source gives the rational-history carriers and
positive-denominator rows, while the $\RegSeqRat$ spine gives the finite
dyadic-tolerance token.

The FKernel and $\Cont$ unary context laws read distance and absolute value at
the same certified observation level. Their output rows therefore have the
same DyadicRatCore shape: rational endpoint carrier, positive denominator,
and the requested dyadic-radius token.

For stability, apply
\autoref{thm:dyadic-rat-core-classifier-obligation}. The
$\mathsf{RatHistoryClassifier}$ comparison and denominator transport carry
input replacement along $\hsame$, and the finite ledger token is preserved by
\autoref{thm:dyadic-rat-core-monotone-radius-obligation} when the metric
request is read at a stronger unary radius.
\end{proof}

\begin{theorem}[DyadicRatCore operation-stability obligation]
\label{thm:dyadic-rat-core-operation-stability-obligation}
The DyadicRatCore source exposes addition, negation, and multiplication
operation-stability only as $\RegSeqRat$ ledger-preserving transformations over
endpoints carrying DyadicRatCore observation rows. Concretely, if the endpoint
histories supplied to one of these operations carry
$\mathsf{DyadicRatCoreObservationRow}$ packages, then the resulting endpoint
row is again a $\mathsf{DyadicRatCoreObservationRow}$ package whose carrier and
classifier faces are read through $\mathsf{RatHistoryClassifier}$ transport and
whose positive denominator face is transported through
$\mathsf{PositiveUnaryDenominator}$. The operation row preserves the recorded
dyadic-radius token of the $\RegSeqRat$ ledger; it does not introduce quotient,
completion, or external metric data.
\end{theorem}
\begin{proof}
Unpack the scoped source package of
\autoref{thm:dyadic-rat-core-scoped-source-package}. Its carrier face is the
rational-history endpoint row together with the positive-denominator row and
the dyadic-radius token recorded in the $\RegSeqRat$ ledger.

The operation rows are therefore read at the level of endpoint histories.
Apply the $\mathsf{RatHistoryClassifier}$ transport face described in
\autoref{thm:dyadic-rat-core-observation-row-classifier-transport} to carry the
rational carrier and classifier data through the addition, negation, or
multiplication row.

The denominator component is carried by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}. Since the
operation stays inside the same certified unary observation request, the
dyadic-radius token remains the ledger token already recorded by
\autoref{thm:dyadic-rat-core-scoped-source-package}.

Repack the transported carrier, classifier, denominator, and ledger token as a
DyadicRatCore observation row. The construction uses only the $\RegSeqRat$
spine and the RatUp endpoint transport, so no quotient or completion datum is
part of the obligation.
\end{proof}

\begin{theorem}[DyadicRatCore radius monotonicity obligation]
\label{thm:dyadic-rat-core-radius-monotonicity-obligation}
The DyadicRatCore dyadic-radius ledger is ordered by certified
$\mathsf{UnaryHistory}$ refinement. If a certified request in a $\RegSeqRat$
spine is refined to a stronger unary request, then the refined request keeps
the endpoint $\mathsf{DyadicRatCoreObservationRow}$ visible, with the same
RatUp carrier face, the transported positive-denominator face, and the refined
dyadic-radius token recorded in the finite ledger bundle.
\end{theorem}
\begin{proof}
Start from the finite ledger extraction theorem
\autoref{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}. It
extracts a DyadicRatCore observation row at each certified unary request of a
finite $\RegSeqRat$ ledger bundle.

For the refined request, use the same finite-bundle induction. The empty bundle
has no endpoint row. In the cons step, compare the displayed request with the
refined request: the matching head request supplies the endpoint row, and the
tail case is handled by the induction hypothesis.

The refined request is then repacked under the scoped source package of
\autoref{thm:dyadic-rat-core-scoped-source-package}. The carrier and
classifier faces are unchanged RatUp endpoint faces, while
\autoref{thm:rat-positive-unary-denominator-hsame-transport} carries the
positive-denominator row along the same $\hsame$ transport.

The monotone radius claim is exactly the persistence of the dyadic-radius token
inside this refined finite ledger. Thus every refined certified unary request
still exposes a DyadicRatCore observation row at the endpoint.
\end{proof}

\begin{theorem}[RegSeqRat dyadic observation coverage]
\label{thm:regseqrat-dyadic-observation-coverage}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ stream certificate spine, and let
$n$ be a certified $\mathsf{UnaryHistory}$ observation index of that spine. Then
the exposed endpoint $s(n)$ has a DyadicRatCore observation row in the sense of
\autoref{def:dyadic-rat-core-observation-row}. Moreover, if a stream classifier
is transported pointwise along $\hsame$ to a target endpoint $s'(n)$, then the
same pointwise transport carries this DyadicRatCore observation row to
$s'(n)$.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:regseqrat-stream-certificate-spine}. At the
certified observation index $n$, \autoref{thm:regseqrat-carrier-obligation}
supplies the endpoint $\mathsf{RatHistoryCarrier}(s(n))$ row and the
dyadic-tolerance witness recorded in the regularity ledger.

The positive-denominator component is read from the RatUp carrier interface:
\autoref{thm:rat-history-carrier-positive-denominator-equivalence} converts the
endpoint carrier row into $\mathsf{PositiveUnaryDenominator}(s(n))$. These
three pieces are exactly the DyadicRatCore observation row of
\autoref{def:dyadic-rat-core-observation-row}.

For the transported endpoint, apply
\autoref{thm:regseqrat-classifier-obligation} to recover the pointwise
$\mathsf{RatHistoryClassifier}$ row carried by the stream classifier. Its
$\hsame$ comparison transports the endpoint carrier/classifier face through the
existing $\mathsf{RatHistoryClassifier}$ transport, and
\autoref{thm:rat-positive-unary-denominator-hsame-transport} transports the
positive-denominator row to $s'(n)$.

The dyadic-radius token is attached to the same certified observation request
in the spine ledger, so no additional completion or quotient datum is needed.
Thus the transported package is again a DyadicRatCore observation row.
\end{proof}

\begin{theorem}[DyadicRatCore observation row finite-ledger extraction]
\label{thm:dyadic-rat-core-observation-row-finite-ledger-extraction}
Let $s:\Hist\to\Hist$ carry a $\RegSeqRat$ stream certificate spine. For every
finite BEDC ledger bundle $L$ of certified $\mathsf{UnaryHistory}$ observation
requests in that spine, there is a finite family indexed by the entries
$n\in L$ whose $n$-th member is a
$\mathsf{DyadicRatCoreObservationRow}(s(n))$ in the sense of
\autoref{def:dyadic-rat-core-observation-row}. This family is read from the
DyadicRatCore scoped source package of
\autoref{thm:dyadic-rat-core-scoped-source-package}; its carrier and classifier
faces are precisely the $\RegSeqRat$ carrier and classifier obligations of
\autoref{thm:regseqrat-carrier-obligation} and
\autoref{thm:regseqrat-classifier-obligation}.

Moreover, if a stream classifier transports the spine pointwise to a target
stream $s':\Hist\to\Hist$, then the same finite family transports endpointwise:
for each certified request $n\in L$, the transported endpoint row is a
$\mathsf{DyadicRatCoreObservationRow}(s'(n))$.
\end{theorem}
\begin{proof}
Induct on the finite ledger bundle $L$. The empty bundle has no certified
observation entry, so the indexed family and its transported endpoint family
are empty.

For a cons bundle, write the displayed head request as the certified
$\mathsf{UnaryHistory}$ observation index $n$ and write $L'$ for the remaining
finite bundle. Apply
\autoref{thm:regseqrat-dyadic-observation-coverage} to the head request in the
$\RegSeqRat$ spine. It supplies the row
$\mathsf{DyadicRatCoreObservationRow}(s(n))$ by unpacking
\autoref{def:dyadic-rat-core-observation-row}, with the carrier datum supplied
by \autoref{thm:regseqrat-carrier-obligation} and the classifier transport
datum supplied by \autoref{thm:regseqrat-classifier-obligation}.

The source package identification in
\autoref{thm:dyadic-rat-core-scoped-source-package} says that no additional
ledger face is used beyond these certified unary observation entries. Therefore
the tail induction hypothesis extracts the finite family over $L'$ from the
same spine and transports it along the same pointwise classifier.

Adjoin the head row to the tail family. The transported head row is provided by
the transported clause of
\autoref{thm:regseqrat-dyadic-observation-coverage}, and the transported tail is
the induction hypothesis. Hence the cons bundle extracts and transports the
claimed finite family endpointwise.
\end{proof}

\begin{theorem}[RegSeqRat constant and transport obligation]
\label{thm:regseqrat-constant-and-transport-obligation}
The constant and transport obligations for $\RegSeqRat$ are the inhabitation of
the constant rational-observation stream and pointwise $\hsame$ transport of
stream classifiers. For every $d:\Hist$ with
$\mathsf{RatHistoryCarrier}(d)$, $\mathsf{RatConstStream}_d$ carries a
$\RegSeqRat$ spine. If $s,t$ are classified streams and $s',t'$ are pointwise
$\hsame$ transports over certified unary observations, then the transported
stream-name classifier $\mathsf{RatStreamNameClassifier}(s',t')$ is part of
the same obligation set.
\end{theorem}
\begin{proof}
Definition~\ref{def:regseqrat-stream-certificate-spine} identifies the
constant case as a spine over a stream-name carrier plus a regularity ledger.
Apply \autoref{thm:regseqrat-constant-stream-spine} to the supplied
$\mathsf{RatHistoryCarrier}(d)$; the resulting ledger is constant at every
certified unary observation.

For transport, apply
\autoref{thm:regseqrat-stream-classifier-stability-spine} to the two endpoint
$\hsame$ rows. It supplies the transported pointwise $\RatUp$ classifiers and
repackages them as $\mathsf{RatStreamNameClassifier}(s',t')$.

The scoped package
\autoref{thm:regseqrat-stream-spine-scoped-package} places the constant and
transport clauses in one certificate package, and
\autoref{thm:regseqrat-realup-seal-consumes-stream-spine} shows that these
clauses are sufficient for the downstream RealUp seal to consume the stream
classifier.
\end{proof}

\begin{theorem}[RegSeqRat dyadic ledger and RealUp seal obligation]
\label{thm:regseqrat-dyadic-ledger-and-real-seal-obligation}
The dyadic-ledger and $\RealUp$ seal obligation for $\RegSeqRat$ consists of
finite unary observation indices, the endpoint $\RatUp$ rows read at those
indices, the dyadic-tolerance witnesses used by regularity, and the seal export
of the recorded $\mathsf{RealUnaryStreamClassifier}$ row. Whenever sealed
$\RealUp$ candidates expose streams satisfying the $\RegSeqRat$ spine and
record their stream comparison row, the seal exports the RealUp observation
classifier required by \autoref{def:real-classifier-specification}.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:regseqrat-stream-certificate-spine}. Its ledger is
finite at the level of requested unary observations and dyadic-tolerance
checks, and each ledger entry is backed by endpoint $\RatUp$ carrier and
classifier rows.

The constant ledger is supplied by
\autoref{thm:regseqrat-constant-stream-spine}. The general endpoint and
transport rows are supplied by
\autoref{thm:regseqrat-stream-classifier-stability-spine}, while
\autoref{thm:regseqrat-stream-spine-scoped-package} gathers the ledger,
classifier, constant, and transport faces as one scoped certificate package.

Finally apply \autoref{thm:regseqrat-realup-seal-consumes-stream-spine}. The
seal reads the already recorded
$\mathsf{RealUnaryStreamClassifier}$ row and exports exactly the observation
classifier required by the RealUp boundary, without adding quotient or
completion data.
\end{proof}
