\begin{theorem}[Real unary stream classifier stability package]
\label{thm:real-unary-stream-classifier-stability-package}
For rational-observation maps $s,t,u,s',t':\Hist\to\Hist$, suppose
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameCarrier}(u),
$$
$$
\mathsf{RealUnaryStreamClassifier}(s,t),\quad
\mathsf{RealUnaryStreamClassifier}(t,u),
$$
and suppose the endpoint transports are pointwise over unary observations:
$$
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(s(n),s'(n)),
\quad
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(t(n),t'(n)).
$$
Then the same BEDC unary observation rows supply the following stability
package:
\begin{enumerate}
  \item $\mathsf{RatStreamNameClassifier}(s,t)$.
  \item $\mathsf{RealUnaryStreamClassifier}(s,s)$,
  $\mathsf{RealUnaryStreamClassifier}(t,s)$, and
  $\mathsf{RealUnaryStreamClassifier}(s,u)$.
  \item For every certified unary observation $n$, both endpoint RatUp carrier
  rows $\mathsf{RatHistoryCarrier}(s(n))$ and
  $\mathsf{RatHistoryCarrier}(t(n))$.
  \item $\mathsf{RealUnaryStreamClassifier}(s',t')$.
\end{enumerate}
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:rat-stream-name-carrier},
Definition~\ref{def:rat-stream-name-classifier}, and
Definition~\ref{def:real-unary-observation-stream-classifier}. After this
unfolding, both StreamNameUp and RealUp classifier rows are the same pointwise
RatUp classifier over histories $n$ equipped with
$\mathsf{UnaryHistory}(n)$.

The first conclusion is therefore just the displayed
$\mathsf{RealUnaryStreamClassifier}(s,t)$ read under the StreamNameUp
classifier name. For $\mathsf{RealUnaryStreamClassifier}(s,s)$, fix a
certified observation $n$; the carrier row for $s$ gives
$\mathsf{RatHistoryCarrier}(s(n))$, and RatUp classifier reflexivity gives the
required point classifier at that observation.

For the reversed classifier $\mathsf{RealUnaryStreamClassifier}(t,s)$, read the
point classifier from $\mathsf{RealUnaryStreamClassifier}(s,t)$ and apply RatUp
classifier symmetry. For $\mathsf{RealUnaryStreamClassifier}(s,u)$, read the
two point classifiers from the assumptions at the same certified observation
and compose them by RatUp classifier transitivity.

For endpoint carriers, fix a certified unary observation $n$ and unpack the
RatUp classifier obtained from $\mathsf{RealUnaryStreamClassifier}(s,t)$ at
that observation. Its endpoint data are precisely
$\mathsf{RatHistoryCarrier}(s(n))$ and $\mathsf{RatHistoryCarrier}(t(n))$.

For transport, fix the same certified observation $n$. Apply
$\mathsf{RatHistoryClassifier\_hsame\_transport}$ to the point classifier from
$\mathsf{RealUnaryStreamClassifier}(s,t)$ and to the two pointwise $\hsame$
witnesses from $s,t$ to $s',t'$. Repacking the transported point classifier
over all certified unary observations gives
$\mathsf{RealUnaryStreamClassifier}(s',t')$.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamClassifier\_streamName\_stability\_package}

\begin{theorem}[Real unary stream-name transported classifier]
\label{thm:real-unary-streamname-transported-classifier}
For rational-observation maps $s,t,s',t':\Hist\to\Hist$, suppose
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RealUnaryStreamClassifier}(s,t),
$$
and suppose the endpoint transports are pointwise over unary observations:
$$
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(s(n),s'(n)),
\quad
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(t(n),t'(n)).
$$
Then $\mathsf{RatStreamNameClassifier}(s',t')$.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:rat-stream-name-carrier},
Definition~\ref{def:rat-stream-name-classifier}, and
Definition~\ref{def:real-unary-observation-stream-classifier}. The
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row supplies the RatUp point
classifier at each certified unary observation, while the two displayed
carrier hypotheses supply the endpoint stream carriers before transport.

Fix a certified unary observation $n$ with witness
$\nu:\mathsf{UnaryHistory}(n)$. Apply
\autoref{thm:rat-history-classifier-hsame-transport} to the RatUp point
classifier read from $\mathsf{RealUnaryStreamClassifier}(s,t)$ at $(n,\nu)$
and to the two pointwise $\hsame$ witnesses from $s,t$ to $s',t'$. This gives
$\mathsf{RatHistoryClassifier}(s'(n),t'(n))$.

Read the endpoint carrier fields of this transported RatUp classifier. The
left field gives $\mathsf{RatHistoryCarrier}(s'(n))$ and the right field gives
$\mathsf{RatHistoryCarrier}(t'(n))$. Since $(n,\nu)$ was arbitrary, these
fields build $\mathsf{RatStreamNameCarrier}(s')$ and
$\mathsf{RatStreamNameCarrier}(t')$.

The same transported RatUp point classifier, again for arbitrary $(n,\nu)$,
supplies the pointwise classifier row of
$\mathsf{RatStreamNameClassifier}(s',t')$. Repack that pointwise row with the
two transported stream carriers to obtain the claimed StreamNameUp
classifier.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamClassifier\_streamName\_transport}

\begin{theorem}[RegSeqRat stream-name scoped interface]
\label{thm:regseqrat-streamname-scoped-interface}
For rational-observation maps $s,t,u,s',t':\Hist\to\Hist$, suppose
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameCarrier}(u),
$$
$$
\mathsf{RealUnaryStreamClassifier}(s,t),\quad
\mathsf{RealUnaryStreamClassifier}(t,u),
$$
and suppose the endpoint transports are pointwise over unary observations:
$$
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(s(n),s'(n)),
\quad
\forall n,\ \mathsf{UnaryHistory}(n)\to\hsame(t(n),t'(n)).
$$
Then these rows determine a scoped $\RegSeqRat$ interface package containing:
\begin{enumerate}
  \item $\mathsf{RatStreamNameClassifier}(s,t)$.
  \item $\mathsf{RealUnaryStreamClassifier}(s,s)$,
  $\mathsf{RealUnaryStreamClassifier}(t,s)$, and
  $\mathsf{RealUnaryStreamClassifier}(s,u)$.
  \item For every certified unary observation $n$, endpoint $\RatUp$
  carrier rows for $s(n)$ and $t(n)$.
  \item $\mathsf{RealUnaryStreamClassifier}(s',t')$.
  \item $\mathsf{RatStreamNameClassifier}(s',t')$.
\end{enumerate}
\end{theorem}
\begin{proof}
Apply Theorem~\ref{thm:real-unary-stream-classifier-stability-package} to
the three stream-name carrier rows, the two RealUp unary classifier rows, and
the two pointwise $\hsame$ transport rows. Its conclusions supply the
StreamNameUp classifier for $(s,t)$, the reflexive, reversed, and composed
RealUp unary classifier rows, the endpoint $\RatUp$ carrier rows at every
certified unary observation, and the transported RealUp unary classifier
for $(s',t')$.

It remains to obtain the transported StreamNameUp classifier. Apply
Theorem~\ref{thm:real-unary-streamname-transported-classifier} with the same
carrier rows for $s$ and $t$, the same
$\mathsf{RealUnaryStreamClassifier}(s,t)$ row, and the same pointwise
$\hsame$ transports from $s,t$ to $s',t'$. This yields
$\mathsf{RatStreamNameClassifier}(s',t')$, which is the final row of the
scoped $\RegSeqRat$ interface package.
\end{proof}

The ten-field fit is: traditional target transport of a unary real stream-name
classifier; BEDC source StreamNameUp read through the RealUp unary classifier;
carrier the transported RatUp endpoint carrier rows for $s'$ and $t'$;
classifier the transported RatUp point classifier; stability pointwise
$\hsame$ transport along unary observations; ledger the observation witness
and the two endpoint transport witnesses; core theorem this block; exactness
$\mathsf{RatStreamNameClassifier}(s',t')$ rather than only
$\mathsf{RealUnaryStreamClassifier}(s',t')$; standard bridge the downstream
RealUp certificate boundary; status $\mathsf{ProofTarget}$.

\begin{definition}[Real ledger policy]
\label{def:real-ledger-policy}
Record finite stream observations, dyadic comparison witnesses, regularity certificates, and classifier comparison certificates when sameness is used.
\end{definition}

\begin{definition}[RealUp certificate obligations]
\label{def:real-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the required fields for using the interface name $\RealUp$.
\end{definition}

\paragraph{Primitive boundary.}
$\RealUp$ is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:real-zero-axiom-note}
The interface avoids quotient machinery. It does not use $\mathsf{Quot.sound}$; sameness is carried by dyadic comparison certificates and the $\RegSeqRat$ classifier.
\end{remark}

\begin{theorem}[RealUp carrier and classifier obligations]
\label{thm:realup-obligation-carrier-classifier}
The $\RealUp$ carrier and classifier obligation set consists exactly of the
sealed $\RegSeqRat$ stream spine, the constant-history carrier
$\mathsf{RealConstantHistoryCarrier}$, the endpoint $\RatUp$ carrier rows, and
the classifier row
$\mathsf{RealConstantHistoryClassifier}$ or
$\mathsf{RealUnaryStreamClassifier}$ read through
\autoref{def:real-carrier},
\autoref{def:real-constant-history-carrier},
\autoref{def:real-classifier-specification}, and
\autoref{def:regseqrat-stream-certificate-spine}. This is the carrier and
classifier part of the $\RealUp$ obligation boundary.
\end{theorem}
\begin{proof}
Use the roadmap ten-field template with traditional target $\RealUp$. The
BEDC source is the DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, and $\RatUp$
interface over $\Hist$; no quotient carrier is introduced outside those
named interfaces.

The carrier choice is the sealed $\RegSeqRat$ stream spine together with
$\mathsf{RealConstantHistoryCarrier}$ and the endpoint $\RatUp$ carrier rows.
Definitions~\ref{def:real-carrier} and
\ref{def:real-constant-history-carrier} name the constant-history side, while
Definition~\ref{def:regseqrat-stream-certificate-spine} names the stream
spine being sealed.

The classifier choice is read from
Definition~\ref{def:real-classifier-specification}: constants use
$\mathsf{RealConstantHistoryClassifier}$ and unary stream observations use
$\mathsf{RealUnaryStreamClassifier}$. Stability obligations, ledger rows,
core theorem list, and exactness predicate are not supplied by this block;
they are the remaining $\RealUp$ obligations. No standard bridge is claimed,
and the status of this theorem is the paper-side carrier and classifier
obligation inventory.
\end{proof}

\begin{theorem}[RealUp stability and transport obligations]
\label{thm:realup-obligation-stability-transport}
The $\RealUp$ stability obligation set is supplied by the
constant-history classifier equivalence fields, endpoint transport, unary
stream classifier stability, the stream-name transported classifier, and
$\RegSeqRat$ transport. Concretely, the required rows are those supplied by
\autoref{thm:real-constant-history-classifier-equivalence-fields},
\autoref{thm:real-constant-history-classifier-endpoint-transport},
\autoref{thm:real-unary-stream-classifier-stability-package}, and
\autoref{thm:real-unary-streamname-transported-classifier}, read over the
same $\Hist$-indexed DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, and
$\RatUp$ sources.
\end{theorem}
\begin{proof}
The traditional target is again $\RealUp$, with BEDC source
DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, and $\RatUp$ over $\Hist$.
The carrier choice and classifier choice are the rows fixed in
\autoref{thm:realup-obligation-carrier-classifier}; this proof names the
stability and transport rows attached to them.

For the constant-history face, apply
\autoref{thm:real-constant-history-classifier-equivalence-fields} to obtain
the reflexive, symmetric, and transitive classifier fields, and apply
\autoref{thm:real-constant-history-classifier-endpoint-transport} to move the
endpoint classifier along $\hsame$ rows.

For the unary stream face, apply
\autoref{thm:real-unary-stream-classifier-stability-package}. It gives the
StreamNameUp classifier, the reflexive, reversed, and composed
$\RealUp$ unary classifier rows, endpoint $\RatUp$ carrier rows, and
transport of $\mathsf{RealUnaryStreamClassifier}$ along pointwise $\hsame$.

Finally, apply
\autoref{thm:real-unary-streamname-transported-classifier} to read the
transported RealUp unary classifier as the transported StreamNameUp
classifier. The ledger and seal are left to the ledger theorem below, the
exactness predicate is classifier preservation along the displayed
transports, no standard bridge is claimed, and the status is the paper-side
stability and transport obligation inventory.
\end{proof}

\begin{theorem}[RealUp ledger and seal obligations]
\label{thm:realup-obligation-seal-ledger}
The $\RealUp$ ledger obligation is exactly the finite unary-observation
ledger together with the dyadic-tolerance requests consumed by the
$\RealUp$ seal. The ledger rows are those named in
\autoref{def:real-ledger-policy}, and the seal consumes precisely the scoped
$\RegSeqRat$ spine supplied by
\autoref{thm:regseqrat-stream-spine-scoped-package} through
\autoref{thm:regseqrat-realup-seal-consumes-stream-spine}.
\end{theorem}
\begin{proof}
Use the same roadmap template. The traditional target is $\RealUp$; the BEDC
source is the DyadicRatCore and $\RegSeqRat$ stream data over $\Hist$, read
through $\StreamNameUp$ names and endpoint $\RatUp$ rows. The carrier and
classifier choices are the rows fixed by
\autoref{thm:realup-obligation-carrier-classifier}.

The ledger is the finite policy of
\autoref{def:real-ledger-policy}: stream observations, dyadic comparison
witnesses, regularity certificates, and classifier comparison certificates.
These are the only ledger rows available to the seal.

Apply \autoref{thm:regseqrat-stream-spine-scoped-package} to collect the
scoped $\RegSeqRat$ carrier, classifier, stability, and finite ledger faces.
Then apply \autoref{thm:regseqrat-realup-seal-consumes-stream-spine}; the
seal reads that scoped spine and its dyadic-tolerance requests without adding
another source of data.

The core theorem list is the scoped spine theorem followed by the seal
consumption theorem. The exactness predicate is equality of consumed data:
the $\RealUp$ seal consumes the finite unary-observation ledger and the
dyadic-tolerance requests displayed by the spine. No standard bridge is
claimed, and the status is the paper-side ledger, seal, and
$\RegSeqRat$-consumption obligation inventory.
\end{proof}

\begin{theorem}[RealUp scoped certificate boundary]
\label{thm:realup-scoped-certificate-boundary}
The scoped $\RealUp$ certificate boundary is exactly the package formed from
\autoref{thm:realup-obligation-carrier-classifier},
\autoref{thm:realup-obligation-stability-transport},
\autoref{thm:realup-obligation-seal-ledger},
\autoref{thm:real-stream-prefix-carrier-obligation},
\autoref{thm:real-stream-prefix-classifier-obligation},
\autoref{thm:real-stream-prefix-stability-obligation}, and
\autoref{thm:real-stream-prefix-ledger-seal-obligation}. Its primitives are
DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, $\RatUp$,
$\mathsf{UnaryHistory}$, $\hsame$ transport,
$\mathsf{RealConstantHistoryCarrier}$,
$\mathsf{RealConstantHistoryClassifier}$,
$\mathsf{RealUnaryStreamClassifier}$, and $\mathsf{RealLedgerPolicy}$.
Within this boundary every carrier, classifier, stability, transport, ledger,
and seal face is read from the same $\Hist$-indexed stream spine and finite
ledger. The boundary contains no quotient data, completion data, arithmetic or
order closure, metric-completeness certificate, or standard-bridge data.
\end{theorem}
\begin{proof}
We first collect the direct $\RealUp$ obligation faces. Apply
\autoref{thm:realup-obligation-carrier-classifier} for the sealed
$\RegSeqRat$ carrier and the constant-history and unary stream classifiers.
Apply \autoref{thm:realup-obligation-stability-transport} for $\hsame$
transport, endpoint transport, and unary stream classifier stability. Apply
\autoref{thm:realup-obligation-seal-ledger} for the finite ledger and the seal
that consumes the scoped stream spine.

We then identify those faces with the stream-prefix obligation inventory.
Apply \autoref{thm:real-stream-prefix-carrier-obligation} for the
DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, and $\RatUp$ carrier source.
Apply \autoref{thm:real-stream-prefix-classifier-obligation} for the
constant-history and unary stream classifier source. Apply
\autoref{thm:real-stream-prefix-stability-obligation} for the pointwise
$\hsame$ stability rows. Apply
\autoref{thm:real-stream-prefix-ledger-seal-obligation} for the finite
ledger policy and seal rows.

The two collections name the same data, because every row is indexed by the
same $\Hist$ stream spine and every ledger entry is one of the finite
$\mathsf{RealLedgerPolicy}$ entries consumed by the seal. Thus the package is
scoped over the displayed BEDC primitives rather than over an external real
object.

Nothing in the construction supplies quotient representatives, a completion
object, arithmetic or order laws, metric completeness, or a standard bridge.
Those data are outside the scoped certificate boundary claimed here.
\end{proof}

\begin{theorem}[RealUp public certificate export]
\label{thm:realup-public-certificate-export}
The public $\NameCert_{\RealUp}$ surface exported to downstream L10 chapters is
exactly the package consisting of
\autoref{thm:realup-scoped-certificate-boundary},
\autoref{thm:realup-scoped-finite-window-read-surface}, the scoped
$\RegSeqRat$ stream-name interface of
\autoref{thm:regseqrat-streamname-scoped-interface}, the DyadicRatCore
observation rows, $\mathsf{RealConstantHistoryCarrier}$,
$\mathsf{RealConstantHistoryClassifier}$,
$\mathsf{RealUnaryStreamClassifier}$, and $\mathsf{RealLedgerPolicy}$.
Downstream chapters may cite this theorem as the public $\RealUp$ certificate
boundary for carrier, classifier, stability, transport, finite observation,
ledger, and seal data. The exported surface contains no completeness theorem,
arithmetic or order closure, metric-completeness certificate, or standard
bridge.
\end{theorem}
\begin{proof}
Start with the scoped certificate boundary. Apply
\autoref{thm:realup-scoped-certificate-boundary}; it gathers the
DyadicRatCore, $\RegSeqRat$, $\StreamNameUp$, $\RatUp$,
$\mathsf{UnaryHistory}$, $\hsame$ transport, constant-history carrier,
constant-history classifier, unary stream classifier, and finite ledger policy
as one $\Hist$-indexed $\RealUp$ boundary.

Next attach the finite read surface. Apply
\autoref{thm:realup-scoped-finite-window-read-surface}; it says that selected
finite $\RealUp$ observation windows read exactly the same carrier/classifier,
stability/transport, finite ledger, dyadic source, stream-name, endpoint, and
seal rows, and no quotient, completion, arithmetic, order, Classical, or
standard-bridge datum.

Finally package the source interfaces exposed to downstream chapters. The
scoped $\RegSeqRat$ stream-name interface of
\autoref{thm:regseqrat-streamname-scoped-interface} supplies the stream-name
classifier, reflexive, reversed, composed, endpoint, and transported
classifier rows. The DyadicRatCore observation rows and the named
$\mathsf{RealConstantHistoryCarrier}$,
$\mathsf{RealConstantHistoryClassifier}$,
$\mathsf{RealUnaryStreamClassifier}$, and $\mathsf{RealLedgerPolicy}$ rows are
therefore precisely the public $\NameCert_{\RealUp}$ surface. Since each row is
already inside the scoped boundary or the finite read surface, downstream L10
chapters may cite this theorem as the public $\RealUp$ certificate boundary
without reconstructing the package.
\end{proof}

\begin{theorem}[RealUp public export through the StreamNameUp public interface]
\label{thm:realup-public-export-through-streamname-public-interface}
The public $\NameCert_{\RealUp}$ surface of
\autoref{thm:realup-public-certificate-export} factors its countable-name
component through the public $\StreamNameUp$ export package of
\autoref{thm:streamname-public-interface-export-package} and factors its
finite-window component through
\autoref{thm:realup-finite-window-export-through-streamname-interface}. After
these two factorizations, the remaining public $\RealUp$ rows are exactly the
DyadicRatCore observation rows, the $\RegSeqRat$ spine rows, the $\RatUp$
endpoint rows, $\mathsf{UnaryHistory}$, $\hsame$ transport,
$\mathsf{RealConstantHistoryCarrier}$,
$\mathsf{RealConstantHistoryClassifier}$,
$\mathsf{RealUnaryStreamClassifier}$, and $\mathsf{RealLedgerPolicy}$.

The factorized public surface still contains no quotient datum, completion
datum, arithmetic or order closure, metric-completeness certificate, Classical
datum, or standard bridge.
\end{theorem}
\begin{proof}
Start from \autoref{thm:realup-public-certificate-export}. It identifies the
public $\NameCert_{\RealUp}$ boundary as the scoped $\RealUp$ certificate
boundary together with the selected finite-window read surface, the
$\RegSeqRat$ stream-name interface, the DyadicRatCore observation rows, and the
named constant-history, unary-stream, transport, endpoint, and ledger rows.

Next isolate the public stream-name package. Apply
\autoref{thm:streamname-public-interface-export-package}; its countable-name
side supplies the $\mathsf{RatStreamNameCarrier}$,
$\mathsf{RatStreamNameClassifier}$, RatUp pointwise rows, constant stream rows,
reindexing and RatUp-preserving map stability, and unary reindexing composition
used by the $\RealUp$ export.

For finite observations, apply
\autoref{thm:realup-finite-window-export-through-streamname-interface}. It
identifies the selected finite $\RealUp$ read surface with the public
$\StreamNameUp$ finite-window interface and leaves only the listed dyadic,
$\RegSeqRat$, endpoint, unary-history, $\hsame$, and ledger rows outside the
stream-name factor.

Finally use \autoref{thm:regseqrat-streamname-scoped-interface} and
\autoref{thm:dyadicratcore-public-observation-package}. The former supplies the
regular rational-stream spine and transported stream-name rows consumed by
$\RealUp$, while the latter supplies the DyadicRatCore observation package.
Thus the public export factors through the two StreamNameUp interfaces and the
unfactored rows are precisely the displayed $\RealUp$ carrier, classifier,
transport, endpoint, history, and ledger rows.
\end{proof}

\begin{theorem}[RealUp Phase Real and Completion boundary]
\label{thm:realup-phase-real-completion-boundary}
The Phase Real and Completion paper boundary is exactly the composite of the
following four public packages:
\begin{enumerate}
  \item the DyadicRatCore public observation package of
  \autoref{thm:dyadicratcore-public-observation-package};
  \item the $\StreamNameUp$ public countable-name export package of
  \autoref{thm:streamname-public-interface-export-package} together with the
  finite-window interface of
  \autoref{thm:streamname-public-finite-window-interface};
  \item the $\RegSeqRat$ stream-name scoped interface of
  \autoref{thm:regseqrat-streamname-scoped-interface};
  \item the $\RealUp$ public certificate export of
  \autoref{thm:realup-public-certificate-export} after factorization through
  the $\StreamNameUp$ public interface in
  \autoref{thm:realup-public-export-through-streamname-public-interface}.
\end{enumerate}
Equivalently, its roadmap ten-field row has traditional target regular real
completion by dyadic rational streams; BEDC source the DyadicRatCore,
$\StreamNameUp$, $\RegSeqRat$, and $\RealUp$ packages listed above; carrier the
DyadicRatCore observations, rational stream names, regular stream spine, and
$\mathsf{RealConstantHistoryCarrier}$ rows; classifier the public
$\StreamNameUp$ classifier, the transported $\RegSeqRat$ stream classifier, and
$\mathsf{RealConstantHistoryClassifier}$ with
$\mathsf{RealUnaryStreamClassifier}$; stability the $\hsame$, endpoint,
stream-name, finite-window, and unary-stream transport rows exposed by those
packages; ledger the finite dyadic observation rows and
$\mathsf{RealLedgerPolicy}$; core theorem list exactly the six displayed
source theorems; exactness finite-window and public-export exactness only up to
the named classifiers; standard bridge absent; status paper-level phase
boundary for the future namespace $\mathsf{BEDC.Derived.RealUp}$.

The boundary contains no $\RealUp$ completeness theorem, no full $\RealUp$
arithmetic or order closure, no metric-completeness certificate, no quotient
construction, no Classical datum, and no standard bridge.
\end{theorem}
\begin{proof}
First collect the four public package faces. Apply
\autoref{thm:dyadicratcore-public-observation-package} for the finite dyadic
observation source. Apply
\autoref{thm:streamname-public-interface-export-package} and
\autoref{thm:streamname-public-finite-window-interface} for the public
countable-name and finite-window surfaces. Apply
\autoref{thm:regseqrat-streamname-scoped-interface} for the regular
rational-stream spine.

Next attach the $\RealUp$ export. Apply
\autoref{thm:realup-public-certificate-export} to read the scoped $\RealUp$
certificate boundary as a public downstream package. Apply
\autoref{thm:realup-public-export-through-streamname-public-interface} to
factor its countable-name and finite-window components through the public
$\StreamNameUp$ interfaces, leaving precisely the dyadic, regular-stream,
endpoint, unary-history, $\hsame$, carrier, classifier, and ledger rows named
in the statement.

Finally repack the collected rows using the roadmap ten-field template. The
traditional target, BEDC source, carrier, classifier, stability, ledger, core
theorem list, exactness, standard-bridge field, and status field are all read
from the cited public packages. Since each cited package explicitly withholds
quotient, completion, arithmetic, order, metric-completeness, Classical, and
standard-bridge data, the composite phase boundary withholds exactly those data
as well.
\end{proof}

\begin{closurestatus}{\RegSeqRat}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The rational-stream certificate spine binds $\RatUp$, $\StreamNameUp$, $\mathsf{UnaryHistory}$, $\hsame$ transport, $\mathsf{RealUnaryStreamClassifier}$, the dyadic-tolerance ledger, and the $\RealUp$ seal as the visible $\RegSeqRat$ scope.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RealUp.RealUnaryStreamClassifier\_streamName\_stability\_package}
  \bridgestatus{none}
  \notclaimed{The scope does not close $\RealUp$ completeness, $\RealUp$ arithmetic or order, full $\DyadicRatCore$ arithmetic, metric completeness, or any standard bridge.}
  \upgradepath{A stronger closure grade requires public $\RealUp$ arithmetic, order, completeness, and standard-bridge certificates beyond this rational-stream certificate boundary.}
\end{closurestatus}

\begin{closurestatus}{\RealUp}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public package is exactly the composite of \autoref{thm:realup-public-certificate-export}, \autoref{thm:realup-public-export-through-streamname-public-interface}, and \autoref{thm:realup-phase-real-completion-boundary}, over DyadicRatCore, $\StreamNameUp$, $\RegSeqRat$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, the finite-window ledger, carrier/classifier, and seal rows.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RealUp.RealConstant\_rational\_embedding\_certificate}
  \bridgestatus{none}
  \notclaimed{This block does not close $\RealUp$ completeness, full arithmetic or order closure, metric completeness, quotient construction, Classical data, or any standard-model bridge.}
  \upgradepath{The next closure grade requires an explicit bridge theorem beyond the public $\RealUp$ export.}
\end{closurestatus}
