\section{Certificate surface}
\label{sec:dyadicratcore-certificate}

\begin{theorem}[DyadicRatCore arithmetic-window stability]
\label{thm:dyadicratcore-arithmetic-window-stability}
Let $D_0,D_1,D'_0,D'_1$ be accepted $\DyadicRatCoreUp$ packets such that
each $D_i$ is transported to $D'_i$ by displayed $\hsame$, $\Cont$, and
$\Pkg$ rows. Any finite common-exponent window that reads $D_0+D_1$,
$-D_0$, $D_0-D_1$, or $D_0D_1$ is stable under this transport: the
transported window reads the corresponding operation on $D'_0,D'_1$ using
only the displayed $\RatUp$ mantissa rows, $\UnaryHistory$ exponent rows,
denominator ledgers, common-exponent scaling rows, $\hsame$ comparisons,
$\Cont$ routes, and $\Pkg$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreArithmeticWindow\_transport\_stability}
\begin{proof}
Choose the displayed common exponent carried by the arithmetic window. The
window first projects the two mantissas to that exponent through the visible
denominator ledgers and then applies the corresponding $\RatUp$ row for sum,
negation, difference, or product.

Transport the mantissa, exponent, denominator, and provenance coordinates of
each input packet along the supplied $\hsame$ rows. The same finite $\Cont$
route transports the common-exponent scaling ledger, so the transported
window has exactly the rows needed to repeat the arithmetic readback.

No step identifies rational pairs by a quotient or by host equality. The
operation row is therefore recovered by recomposing the transported mantissa
row with the transported unary denominator ledger and the same $\Pkg$ source
certificates.
\end{proof}

\begin{theorem}[DyadicRatCore monotone-radius obligation]
\label{thm:dyadicratcore-monotone-radius-obligation}
For an accepted $\DyadicRatCoreUp$ packet $D=(m,e,\ell,P)$, the visible
dyadic radius row $2^{-e}$ refines monotonically under any displayed unary
extension $e \preceq E$. The refined radius row $2^{-E}$ is obtained by
appending the finite denominator ledger entries from $e$ to $E$, transporting
the mantissa observation through the same $\Cont$ route, and retaining the
same $\Pkg$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_scoped\_source\_boundary}
\begin{proof}
Project the positive unary exponent row from the carrier. A displayed
extension $e \preceq E$ is a finite unary-history continuation, so the
additional denominator entries form a visible tail of the same ledger.

Append that tail to the denominator ledger $\ell$. The resulting row displays
$2^E$ and hence the radius row $2^{-E}$, with the original $2^{-e}$ radius as
the coarser prefix read by the shorter window.

The mantissa row is not changed; only the denominator window is refined.
Transporting the readback through the appended $\Cont$ route shows monotone
radius refinement entirely inside the displayed unary ledger.
\end{proof}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_monotone\_radius\_obligation}

\begin{theorem}[DyadicRatCore scale-window obligation surface]
\label{thm:dyadicratcore-scale-window-obligation-surface}
The canonical common-exponent scale window, monotone radius obligation, denominator ledger, and arithmetic-window stability together provide the exact dyadic tolerance row consumed by $\StreamNameUp$ finite windows and $\RegSeqRatUp$ regularity checks. The consumed row is the visible dyadic packet formed from the signed mantissa, positive unary exponent, denominator ledger, common-exponent scaling row, monotone radius refinement, arithmetic stability row, $\BHist$ carrier data, $\hsame$ transport, $\Cont$ replay, and $\Pkg$ provenance; it is not a quotient rational class, host rational equality, or host real distance.
\end{theorem}
\begin{proof}
First use monotone-radius obligation, \autoref{thm:dyadicratcore-monotone-radius-obligation}. It refines the dyadic radius by appending visible unary denominator entries and keeps the radius row inside the displayed carrier and continuation surface.

Next use common-exponent exactness, \autoref{thm:dyadicratcore-common-exponent-exactness}, together with the denominator ledger transport of \autoref{thm:dyadicratcore-denominator-ledger}. These rows put the compared packets on one common exponent while preserving the visible mantissa and denominator-ledger sources.

Then apply arithmetic-window stability, \autoref{thm:dyadicratcore-arithmetic-window-stability}, and the RegSeqRat window-radius handoff, \autoref{thm:dyadicratcore-regseqrat-window-radius-handoff}. The arithmetic and radius windows are the same finite dyadic tolerance packet consumed by StreamName finite windows and RegSeqRat regularity checks.

The cited rows mention only displayed dyadic data, carrier histories, transports, continuations, and provenance. None provides quotient rational classes, host equality, or a host real distance coordinate, so the obligation surface is exact.
\end{proof}

\begin{theorem}[DyadicRatCore arithmetic-monotone window package]
\label{thm:dyadicratcore-arithmetic-monotone-window-package}
Let $D_0,D_1,D'_0,D'_1$ be accepted $\DyadicRatCoreUp$ packets satisfying
the arithmetic-window transport hypotheses of
\autoref{thm:dyadicratcore-arithmetic-window-stability}, and suppose the
visible radius rows of the transported packet are refined along displayed
unary exponent extensions as in
\autoref{thm:dyadicratcore-monotone-radius-obligation}. Then the transported
arithmetic endpoint and the refined radius ledger repack into one public
finite window consumed by $\RegSeqRat$ and $\RealUp$. This window reads only
mantissa, exponent, denominator, common-exponent, distance and arithmetic,
$\mathsf{BHist}$, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows, and it exposes
no quotient rational, host equality, completion endpoint, or trichotomy row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:dyadicratcore-arithmetic-window-stability}. The
transported arithmetic endpoint is read from the common-exponent scaling
ledger, the displayed mantissas, the denominator rows, and the transported
$\Pkg$ provenance.

Next apply \autoref{thm:dyadicratcore-monotone-radius-obligation} to the
visible unary extension of the radius row. The refined denominator ledger
keeps the radius bound inside the same $\mathsf{BHist}$ and $\Cont$ surface.

The two ledgers have the same public coordinates: mantissa, exponent,
denominator, common exponent, arithmetic or distance readback, history
comparison, continuation, and package provenance. Repack those coordinates as
the shared finite-window surface required by the $\RegSeqRat$ and $\RealUp$
consumers. Since neither input theorem exports quotient rational equality,
host equality, a completion endpoint, or a trichotomy classifier, the combined
window does not introduce any such row.
\end{proof}

\begin{theorem}[DyadicRatCore common-exponent exactness]
\label{thm:dyadicratcore-common-exponent-exactness}
Suppose two classifier witnesses compare accepted packets $D$ and $D'$ by
displayed common exponents $E$ and $F$. Then there is a displayed unary
exponent $G$ extending both $E$ and $F$ such that transporting each witness to
$G$ yields the same $\RatUp$ classifier row between the scaled mantissas of
$D$ and $D'$. The exactness claim is a statement about the displayed scaling
ledgers and not about host rational equality.
\end{theorem}
\begin{proof}
Project the two classifier witnesses of
\autoref{def:dyadicratcore-classifier}. Each witness consists of a common
unary exponent, two finite scaling ledgers from the packet exponents, and a
$\RatUp$ classifier row between the scaled mantissas.

Take the displayed unary exponent obtained by appending the two finite
extension ledgers to a shared exponent $G$. Transport the $E$-witness and the
$F$-witness along their denominator-ledger continuations into the same
exponent row.

At $G$ both witnesses read the identical scaled mantissa rows through the
same $\RatUp$ source certificate. Constructor inspection of the transported
classifier rows therefore gives the same visible classifier row, with no
appeal to quotient equality of dyadic pairs.
\end{proof}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreClassifier\_common\_exponent\_e0\_exclusion}

\begin{definition}[DyadicRatCore canonical comparison window]
\label{def:dyadicratcore-canonical-window}
For accepted packets $D$ and $D'$ of $\DyadicRatCoreUp$, the canonical
comparison window is the finite BEDC packet
$$
\begin{gathered}
  (G,\ \Delta_D^G,\ \Delta_{D'}^G,\ M_D^G,\ M_{D'}^G,\
  R_G,\ H_G,\ S_G,\ C_G,\ P_G,\ N_G).
\end{gathered}
$$
Here $G$ is a chosen common positive unary exponent, $\Delta_D^G$ and
$\Delta_{D'}^G$ are the transported denominator ledgers, $M_D^G$ and
$M_{D'}^G$ are the scaled mantissa rows, and $R_G$ is the displayed $\RatUp$
classifier row between those scaled mantissas. The remaining rows $H_G$,
$S_G$, $C_G$, $P_G$, and $N_G$ are the attached $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ provenance carried by the accepted packets and their
transport ledgers. The window is a finite BEDC comparison surface; it is not a
quotient equality of dyadic pairs and not a host rational representative.
\end{definition}

\begin{theorem}[DyadicRatCore canonical-window uniqueness]
\label{thm:dyadicratcore-canonical-window-uniqueness}
If two canonical comparison windows compare the same accepted
$\DyadicRatCoreUp$ packets $D$ and $D'$, then after displayed unary exponent
refinement to a common terminal exponent they expose the same transported
denominator ledgers, scaled mantissa rows, $\RatUp$ classifier row, and
support rows. No quotient rational, host equality, completed $\RealUp$
endpoint, or trichotomy row can distinguish the two windows.
\end{theorem}
\begin{proof}
Unfold \autoref{def:dyadicratcore-canonical-window}. Each window consists of
a common positive unary exponent, two transported denominator ledgers, two
scaled mantissa rows, one $\RatUp$ classifier row, and the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Apply \autoref{thm:dyadicratcore-common-exponent-exactness} to the two
classifier witnesses. Refining both displayed exponents to a common terminal
exponent puts the two comparison rows on the same scaled mantissa surface.

Use \autoref{thm:dyadicratcore-denominator-ledger} to identify the transported
denominator rows after the same exponent refinement. Use
\autoref{thm:dyadicratcore-distance-window-stability} to keep the finite
observation rows stable under the resulting $\hsame$ transport.

It remains only to read the carrier inventory. The available rows are exactly
the mantissa, exponent, denominator, classifier, history, sameness,
continuation, package, and name-certificate rows listed in
\autoref{def:dyadicratcore-carrier}. The exclusions in
\autoref{thm:dyadicratcore-scoped-source-boundary} remove quotient rational
equality, host equality, completed real endpoints, and trichotomy classifiers,
so no additional row can separate the two refined windows.
\end{proof}

\begin{theorem}[DyadicRatCore real-phase source coverage]
\label{thm:dyadicratcore-real-phase-source-coverage}
Every $\StreamNameUp$, $\RegSeqRat$, or $\RealUp$ dyadic observation that
consumes $\DyadicRatCoreUp$ data downstream reads through the mantissa,
positive exponent, denominator ledger, common-exponent classifier,
arithmetic-window, distance-window, monotone-radius, $\hsame$, $\Cont$, and
$\Pkg$ rows listed in this chapter. The source boundary exports no quotient
of dyadic pairs, host rational equality, or completed real endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_real\_phase\_source\_coverage}
\begin{proof}
Start with a downstream dyadic observation in one of the real-construction
interfaces. Its input is an accepted $\DyadicRatCoreUp$ packet, so the only
available source coordinates are the carrier rows of
\autoref{def:dyadicratcore-carrier} and the classifier rows of
\autoref{def:dyadicratcore-classifier}.

Arithmetic and distance observations factor through
\autoref{thm:dyadicratcore-arithmetic-window-stability} and
\autoref{thm:dyadicratcore-distance-window-stability}. Radius observations
factor through \autoref{thm:dyadicratcore-monotone-radius-obligation}, and
classifier comparisons factor through
\autoref{thm:dyadicratcore-common-exponent-exactness}.

These projections exhaust the finite rows named by the downstream readback.
Since no row in the packet carries a quotient class, a host rational equality,
or a completed real endpoint, the real-phase consumer can only use the listed
BEDC source rows.
\end{proof}

\begin{theorem}[DyadicRatCore RegSeqRat window radius handoff]
\label{thm:dyadicratcore-regseqrat-window-radius-handoff}
Every downstream $\RegSeqRat$ finite-window handoff that consumes a
$\DyadicRatCoreUp$ observation reads its radius premise through the displayed
positive unary exponent, denominator ledger, monotone-radius refinement,
distance-window stability, $\hsame$, $\Cont$, and $\mathsf{Pkg}$ rows of the
$\DyadicRatCoreUp$ public envelope. Consequently the handoff cannot introduce
a quotient rational, host epsilon equality, or $\RealUp$ completion endpoint.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreRegSeqRatWindow\_radius\_handoff}
\begin{proof}
Start with the downstream handoff and apply
\autoref{thm:dyadicratcore-real-phase-source-coverage}. The observation can
only read the dyadic packet through the listed source rows and has no access to
a quotient rational or completed real endpoint.

Use \autoref{thm:dyadicratcore-monotone-radius-obligation} to identify the
radius premise as a displayed positive-unary refinement over the denominator
ledger. Use \autoref{thm:dyadicratcore-distance-window-stability} to keep the
finite distance window stable under the same $\hsame$ transport.

Finally apply \autoref{thm:dyadicratcore-public-readback-envelope}. Its public
tuple supplies exactly the exponent, denominator, radius, distance, $\Cont$,
and $\mathsf{Pkg}$ coordinates consumed by $\RegSeqRat$, so there is no
remaining coordinate through which host epsilon equality or a $\RealUp$
completion endpoint could enter the handoff.
\end{proof}

\begin{theorem}[DyadicRatCore NameCert obligation surface]
\label{thm:dyadicratcore-namecert-obligation-surface}
The seed $\NameCert_{\DyadicRatCoreUp}$ obligation surface consists of the
signed mantissa carrier of \autoref{def:dyadicratcore-carrier}, the
common-exponent scaling classifier of
\autoref{def:dyadicratcore-classifier}, denominator ledger transport from
\autoref{thm:dyadicratcore-denominator-ledger}, dyadic distance and
absolute-value window stability from
\autoref{thm:dyadicratcore-distance-window-stability}, arithmetic-window
stability from
\autoref{thm:dyadicratcore-arithmetic-window-stability}, monotone radius
refinement from
\autoref{thm:dyadicratcore-monotone-radius-obligation}, common-exponent
exactness from
\autoref{thm:dyadicratcore-common-exponent-exactness}, real-phase source
coverage from
\autoref{thm:dyadicratcore-real-phase-source-coverage}, and exactness of the
visible mantissa, exponent, denominator, $\hsame$, $\Cont$, and $\Pkg$ rows.
It supplies a named dyadic source surface for $\StreamNameUp$, $\RegSeqRat$,
and $\RealUp$, but it supplies no standard bridge and no $\RealUp$
completeness claim.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_namecert\_obligation\_surface}
\begin{proof}
The carrier and classifier clauses are exactly
\autoref{def:dyadicratcore-carrier} and
\autoref{def:dyadicratcore-classifier}. They determine which finite BEDC rows
may be read as a dyadic packet and how two such packets are compared by
common-exponent scaling.

The ledger clause is
\autoref{thm:dyadicratcore-denominator-ledger}; it keeps the positive unary
denominator tower visible under $\hsame$ transport. The observation clause is
\autoref{thm:dyadicratcore-distance-window-stability}; it keeps distance and
absolute-value windows inside the displayed $\RatUp$ and unary ledger rows.

The arithmetic, radius, common-exponent, and real-phase source clauses are
\autoref{thm:dyadicratcore-arithmetic-window-stability},
\autoref{thm:dyadicratcore-monotone-radius-obligation},
\autoref{thm:dyadicratcore-common-exponent-exactness}, and
\autoref{thm:dyadicratcore-real-phase-source-coverage}. Together they state
which finite rows downstream real-construction chapters may consume and how
those rows refine under displayed unary denominator extension.

Exactness follows by inspection of the listed rows: every readable component
of the dyadic source is one of the mantissa, exponent, denominator,
provenance, transport, or continuation entries. Thus the surface is a seed
source for later real-construction chapters and not a bridge to host rationals
or completed reals.
\end{proof}

\begin{theorem}[DyadicRatCore scoped source boundary]
\label{thm:dyadicratcore-scoped-source-boundary}
The scoped $\DyadicRatCoreUp$ source boundary is exactly the signed $\RatUp$
mantissa row, the positive $\UnaryHistory$ exponent row, the denominator
ledger, the common-exponent scaling classifier, the arithmetic-window and
distance-window rows, monotone-radius refinement, common-exponent exactness,
real-phase source coverage, $\mathsf{BHist}$ carrier data, $\hsame$
transport, $\Cont$ readback, and $\mathsf{Pkg}$ provenance listed in this
chapter. It exports no quotient of dyadic pairs, host rational equality,
standard bridge, or completed $\RealUp$ endpoint.
\end{theorem}
\begin{proof}
The carrier and classifier boundaries are the displayed rows of
\autoref{def:dyadicratcore-carrier} and
\autoref{def:dyadicratcore-classifier}. They supply the signed mantissa,
positive unary exponent, denominator tower, $\mathsf{BHist}$ tuple, $\hsame$
transport, $\Cont$ readback, and $\mathsf{Pkg}$ provenance that can be read
from an accepted dyadic packet.

The denominator, arithmetic, distance, radius, and common-exponent clauses are
respectively \autoref{thm:dyadicratcore-denominator-ledger},
\autoref{thm:dyadicratcore-arithmetic-window-stability},
\autoref{thm:dyadicratcore-distance-window-stability},
\autoref{thm:dyadicratcore-monotone-radius-obligation}, and
\autoref{thm:dyadicratcore-common-exponent-exactness}. These rows say how the
same visible packet supports finite dyadic computation under displayed unary
denominator transport.

The real-phase and NameCert clauses are
\autoref{thm:dyadicratcore-real-phase-source-coverage} and
\autoref{thm:dyadicratcore-namecert-obligation-surface}. They exhaust the
downstream source rows consumed by $\StreamNameUp$, $\RegSeqRat$, and
$\RealUp$ without adding a quotient class, a host-rational equality row, a
standard bridge, or a completed real endpoint. Hence the listed primitives are
precisely the scoped boundary exported by this chapter.
\end{proof}

\begin{theorem}[DyadicRatCore public readback envelope]
\label{thm:dyadicratcore-public-readback-envelope}
The public $\DyadicRatCoreUp$ consumer interface is exactly the tuple
consisting of the signed mantissa carrier, common-exponent classifier,
denominator ledger transport, arithmetic-window stability, distance-window
stability, monotone-radius refinement, common-exponent exactness, real-phase
source coverage, $\mathsf{BHist}$ carrier rows, $\hsame$ transport, $\Cont$
readback, and $\mathsf{Pkg}$ provenance. Every downstream $\StreamNameUp$,
$\RegSeqRat$, or $\RealUp$ dyadic read factors through this envelope and cannot
read a quotient rational, host rational equality, standard bridge, or completed
real endpoint.
\end{theorem}
\begin{proof}
Start with an arbitrary public consumer read of a $\DyadicRatCoreUp$ packet.
By \autoref{def:dyadicratcore-carrier} and
\autoref{def:dyadicratcore-classifier}, the only carrier and comparison rows
available to that read are the signed mantissa, positive unary exponent,
denominator ledger, common-exponent scaling witness, $\mathsf{BHist}$ data,
$\hsame$ rows, $\Cont$ routes, and $\mathsf{Pkg}$ provenance.

The finite denominator, arithmetic, distance, radius, and exactness reads are
then forced through the named certificate rows. Use
\autoref{thm:dyadicratcore-denominator-ledger},
\autoref{thm:dyadicratcore-arithmetic-window-stability},
\autoref{thm:dyadicratcore-distance-window-stability},
\autoref{thm:dyadicratcore-monotone-radius-obligation}, and
\autoref{thm:dyadicratcore-common-exponent-exactness} to identify the visible
rows that remain available under transport and denominator refinement.

Finally apply \autoref{thm:dyadicratcore-real-phase-source-coverage} and
\autoref{thm:dyadicratcore-scoped-source-boundary}. They state that the
downstream $\StreamNameUp$, $\RegSeqRat$, and $\RealUp$ reads consume exactly
this dyadic source surface. Since the carrier inventory contains no quotient
rational, host equality row, standard bridge, or completed real endpoint, none
of those objects can be exported by the public consumer certificate.
\end{proof}
\leanchecked{BEDC.Derived.DyadicRatCoreUp.DyadicRatCoreCarrier\_public\_readback\_envelope}
