$\DyadicRatCoreUp$ reads its signed mantissa row and denominator ledger through the integer and rational certificate surfaces of \autoref{ch:concrete-instances-int-namecert} and \autoref{ch:concrete-instances-rat-namecert}. It then supplies the finite dyadic tolerance ledger consumed by \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}, while exporting no host rational quotient, selected real limit, or $\RealUp$ completeness theorem.

\begin{theorem}[DyadicRatCore L10 sibling dependency totality]
\label{thm:dyadicratcore-l10-sibling-dependency-totality}
Every accepted Phase Real or completion-facing consumer that reaches
$\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ through a dyadic tolerance face
consumes exactly the signed $\RatUp$ mantissa row, positive $\UnaryHistory$
exponent row, denominator ledger, common-exponent classifier,
radius/distance windows, and displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ support supplied by $\DyadicRatCoreUp$. Conversely, those
rows supply the dyadic face required by the $\StreamNameUp$ finite-window
schedule, the $\RegSeqRatUp$ regularity and classifier rows, and the
$\RealUp$ terminal seal. The total route exports no quotient rational
equality, quotient stream equality, host real equality, selected limit,
countable choice, ambient completeness, metric-completeness row, or
$\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
For the consumer-to-dyadic direction, apply
\autoref{thm:dyadicratcore-public-bridge-consumer-exactness}. It identifies
the public dyadic consumer inventory with the signed mantissa, positive unary
exponent, denominator ledger, common-exponent classifier, finite windows,
displayed history and sameness rows, readback, package provenance, and
certificate support already supplied by $\DyadicRatCoreUp$.

The standard-source bridge of
\autoref{thm:dyadicratcore-standard-source-bridge} keeps that inventory fixed
when the dyadic face is presented to sibling consumers. Then
\autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness} gives the
RegSeqRat handoff exactness for the same endpoint, radius, and finite-window
rows.

For the reverse direction, start with precisely those $\DyadicRatCoreUp$
rows. The StreamName terminal pullback of
\autoref{thm:streamname-real-completion-four-object-terminal-pullback}
places the DyadicRatCore face, the finite StreamName schedule, the RegSeqRat
regular source, and the local Real seal in one terminal finite packet.

Finally apply
\autoref{thm:real-dyadic-streamname-regseqrat-dependency-route}. It reads the
ordered route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
and excludes quotient rational or stream equality, host real equality,
selected limits, countable choice, ambient completeness, metric-completeness
rows, and $\RealUp$ completeness from the route. These exclusions are exactly
the non-rows listed in the theorem statement.
\end{proof}

\begin{theorem}[DyadicRatCore StreamName finite-window radius transport]
\label{thm:dyadicratcore-streamname-finite-window-radius-transport}
Whenever a $\StreamNameUp$ finite-window consumer reads a $\DyadicRatCoreUp$
endpoint/radius ledger and then hands the read to a $\RegSeqRatUp$ consumer or
to a $\RealUp$ seal route, the transported finite window preserves the same
signed $\RatUp$ mantissa row, positive $\UnaryHistory$ exponent row,
common-exponent classifier, radius/distance window, and displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support. The transport introduces
no point carrier, quotient rational equality, quotient stream equality,
selected limit, host real equality, countable-choice row, metric-completeness
row, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Start with the endpoint/radius ledger supplied by
\autoref{thm:dyadicratcore-l10-sibling-dependency-totality}. That theorem
identifies the dyadic consumer surface with the signed mantissa, positive unary
exponent, denominator, classifier, finite radius and distance windows, and the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Apply \autoref{thm:streamname-dyadicratcore-window-anchor}. The StreamName
finite-window read is anchored to this dyadic observation ledger before any
downstream consumer can inspect it, so the projection keeps the same rows rather
than replacing them by a detached stream or host-real witness.

For the RegSeqRat handoff, use
\autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness}. It reads the
same endpoint/radius packet as the regular-rational finite window, preserving
the classifier and radius/distance rows already visible through the StreamName
projection.

For the Real seal route, apply
\autoref{thm:real-dyadic-streamname-regseqrat-dependency-route}. Its ordered
route reads the DyadicRatCore face through $\StreamNameUp$ and $\RegSeqRatUp$
before the local $\RealUp$ seal, so the Real-facing packet inherits the same
finite support rows.

The exclusion clauses in these three route theorems rule out every additional
point carrier, quotient rational or stream equality, selected limit, host real
equality, countable-choice row, metric-completeness row, and $\RealUp$
completeness coordinate. Hence the finite-window transport is exactly the
displayed DyadicRatCore radius ledger throughout the StreamName, RegSeqRat, and
Real consumers.
\end{proof}
