\begin{theorem}[Prod finite-data scoped closure record]
\label{thm:prod-finite-data-scoped-closure-record}
The componentwise public certificate, displayed-pair ledger endpoints,
descent-to-envelope row, $\hsame$ and $\Cont$ transports, and $\mathsf{Pkg}$
provenance of \autoref{thm:prod-public-finite-data-exit-package} bind the
$\ProdUp$ finite-data scope entirely inside BEDC histories. More precisely,
for source-history carriers $L,R:\mathsf{BHist}\to\mathsf{Prop}$, source
classifiers $\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$,
source certificates $\mathsf{cert}_L:\NameCert(L,\sim_L)$ and
$\mathsf{cert}_R:\NameCert(R,\sim_R)$, and a
$\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ witness, the public
finite-data package exposes only the componentwise
$\mathsf{SemanticNameCert}$ row, the two displayed-pair ledger endpoints, the
descent row into $\mathsf{ProdHistoryClassifier}(L,R)$, the $\hsame$ and
$\Cont$ endpoint-transport rows, and the $\mathsf{Pkg}$ provenance rows named
by the $\ProdUp$ obligation surface. No host tuple equality is part of the
record.
\end{theorem}
\begin{proof}
Apply \autoref{thm:prod-public-finite-data-exit-package}. Its first row gives
the componentwise public certificate for
$\mathsf{ProdHistoryCarrier}(L,R)$ under
$\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}$, using exactly
the two source $\NameCert$ rows and the displayed-pair coherence witness.

The second and third rows of that package project the displayed-pair ledger
endpoints and the descent-to-envelope comparison for any componentwise
classifier witness between histories $h,k:\mathsf{BHist}$. The target of the
descent is the checked envelope classifier
$\mathsf{ProdHistoryClassifier}(L,R,h,k)$.

The fourth row identifies the remaining public data with the source
certificate rows, the componentwise classifier row, the displayed-pair ledger
row, the descent row, the $\hsame$ and $\Cont$ transport rows, and the
$\mathsf{Pkg}$ provenance rows of
\autoref{thm:produp-obligation-surface-package}. The checked envelope
certificate \autoref{thm:concrete-prod-namecert} supplies the BEDC history
envelope in which those rows land.

Thus the finite-data scope is closed by projections of the public package and
the checked envelope certificate. Every named row is a row over
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\NameCert$, and $\mathsf{Pkg}$, so the
record contains no host tuple equality.
\end{proof}

\begin{theorem}[Prod finite-data consumer row exhaustion]
\label{thm:prod-finite-data-consumer-row-exhaustion}
Any consumer of the public $\ProdUp$ finite-data package can read only the
componentwise $\mathsf{SemanticNameCert}$ row, the displayed-pair ledger
endpoints, descent into $\mathsf{ProdHistoryClassifier}$, the $\hsame/\Cont$
endpoint transports, the source $\NameCert$ rows, and the $\mathsf{Pkg}$
provenance. No host tuple equality, component projection outside the displayed
ledger, or quotient of pair representatives is exported.
\end{theorem}
\begin{proof}
Apply \autoref{thm:prod-public-finite-data-exit-package}. This gives the
consumer-facing package rows: componentwise public certificate, displayed-pair
ledger endpoints, descent to the product-history classifier, endpoint
transports, source certificate rows, and provenance rows.

Next apply \autoref{thm:prod-finite-data-scoped-closure-record} to identify the
closed finite-data scope. That theorem says that the public rows are exactly
the rows bound inside BEDC histories by the product finite-data record.

The absence claim follows by row exhaustion. Since those two packages list the
entire consumer surface and neither package contains host tuple equality,
outside-ledger component projection, or a quotient of pair representatives, no
consumer can project such data from the public $\ProdUp$ finite-data package.
\end{proof}

\begin{theorem}[Prod component ledger endpoint determinacy]
\label{thm:prod-component-ledger-endpoint-determinacy}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers, let
$\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$ be source
classifiers, let $\mathsf{cert}_L:\NameCert(L,\sim_L)$ and
$\mathsf{cert}_R:\NameCert(R,\sim_R)$ be source rows, and let
$\mathsf{coh}:\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ be a displayed
pair-representative coherence witness. If two
$\mathsf{ProdHistoryLedgerChain}(L,R,\rho,z)$ readbacks from the same raw
product row $\rho$ expose component pairs $(l,r)$ and $(l',r')$ through
$\mathsf{ProdPairRep}$, then the public finite-data package forces
$l\sim_L l'$ and $r\sim_R r'$. Consequently the two visible endpoints are
related by $\mathsf{ProdHistoryClassifier}(L,R)$, and no further host-level
tuple equality is needed.
\end{theorem}
\begin{proof}
Apply the displayed component readback to each of the two ledger-chain
readbacks. Both readbacks start from the same raw product row $\rho$, so the
only component witnesses they expose are the two displayed
$\mathsf{ProdPairRep}$ pairs named in the ledger.

Use the coherence witness $\mathsf{coh}$ to compare those two displayed pairs
componentwise. This yields the source classifier rows $l\sim_L l'$ and
$r\sim_R r'$ inside the same BEDC history envelope as the source
$\NameCert$ rows.

Finally repack the two source classifier rows through the product envelope
classifier. The consumer-row exhaustion theorem identifies that envelope row
as part of the public finite-data surface, so the endpoint comparison lands in
$\mathsf{ProdHistoryClassifier}(L,R)$ and exports no outside-ledger component
projection.
\end{proof}

\begin{theorem}[Prod finite-data closure status record]
\label{thm:prod-finite-data-closure-status-record}
The scoped row record of
\autoref{thm:prod-finite-data-scoped-closure-record}, the consumer-row
exhaustion theorem
\autoref{thm:prod-finite-data-consumer-row-exhaustion}, and the endpoint
determinacy theorem
\autoref{thm:prod-component-ledger-endpoint-determinacy}, together with the
checked envelope certificate \autoref{thm:concrete-prod-namecert}, give the
Phase Finite Data scoped closure surface for $\ProdUp$. The resulting surface
is exactly the public finite-data exit package: componentwise semantic
certificate rows, displayed-pair ledger endpoints, descent into
$\mathsf{ProdHistoryClassifier}(L,R)$, $\hsame/\Cont$ transport rows, source
$\NameCert$ rows, and $\mathsf{Pkg}$ provenance.
\end{theorem}
\begin{proof}
Project first through \autoref{thm:prod-public-finite-data-exit-package}. The
finite-data scoped record identifies the rows exported by that package and
places each row inside the BEDC history envelope rather than in host tuple
equality.

Next use \autoref{thm:prod-finite-data-consumer-row-exhaustion}. It says that a
consumer of the package has no access to rows beyond the componentwise
certificate, the displayed-pair ledger endpoints, the descent row, the endpoint
transports, the source certificates, and the provenance rows.

The endpoint determinacy theorem then fixes the visible ledger endpoints by the
source classifiers and repacks them through
$\mathsf{ProdHistoryClassifier}(L,R)$. The checked envelope certificate
\autoref{thm:concrete-prod-namecert} supplies the semantic-name certificate
row for that repacking.

Combining these projections gives the Phase Finite Data scoped closure surface
for $\ProdUp$: every exported row is one of the public finite-data rows, every
endpoint comparison lands in the checked product-history classifier, and no
outside-ledger component projection or host tuple equality is exported.
\end{proof}

\begin{theorem}[Prod finite-data public bridge consumer]
\label{thm:prod-finite-data-public-bridge-consumer}
Every Bool, Option, Sum, or List finite-data consumer of the public $\ProdUp$
package factors through the scoped record
\autoref{thm:prod-finite-data-scoped-closure-record}, the consumer-row
exhaustion theorem
\autoref{thm:prod-finite-data-consumer-row-exhaustion}, endpoint determinacy
\autoref{thm:prod-component-ledger-endpoint-determinacy}, and the public
finite-data exit package
\autoref{thm:prod-public-finite-data-exit-package}. Its visible read is
therefore exhausted by componentwise semantic certificate rows,
displayed-pair ledger endpoints, descent into
$\mathsf{ProdHistoryClassifier}(L,R)$, $\hsame/\Cont$ transport, source
$\NameCert$ rows, and $\mathsf{Pkg}$ provenance. No such consumer receives
host tuple equality or an outside-ledger component projection.
\end{theorem}
\begin{proof}
First project the public package of
\autoref{thm:prod-public-finite-data-exit-package}. A Bool, Option, Sum, or
List consumer reads the componentwise public certificate, the displayed-pair
ledger endpoints, the descent row, the endpoint transports, the source
certificate rows, and the provenance rows from that package.

Next apply the scoped record
\autoref{thm:prod-finite-data-scoped-closure-record}. It places exactly those
rows inside the BEDC history envelope and identifies the product-history
classifier as the endpoint classifier available to finite-data consumers.

Then use consumer-row exhaustion and endpoint determinacy. The exhaustion
theorem removes every row not listed by the public package, and endpoint
determinacy routes visible component endpoints through the product-history
classifier rather than through host tuple equality.

Thus the public finite-data bridge available to Bool, Option, Sum, and List
consumers is precisely the displayed $\ProdUp$ package route. There is no
remaining coordinate from which an outside-ledger projection can be read.
\end{proof}
