\begin{theorem}[ProdUp BHist pair projection determinacy]
\label{thm:prod-bhist-pair-projection-determinacy}
For every accepted $\ProdUp$ public pair read, the $\BHist$ projection is determined by the two displayed component rows together with the product component ledger, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ProdUp}$ row. The finite-data siblings of \autoref{ch:concrete-instances-bool-namecert}, \autoref{ch:concrete-instances-sum-namecert}, and \autoref{ch:concrete-instances-list-namecert} may consume the read only after those product rows have fixed the two projections. Thus the product packet cannot export a tag-only $\SumUp$ branch, optional none row, or $\ListUp$ spine without passing through the corresponding sibling $\NameCert$ surface.
\end{theorem}
\begin{proof}
Start from the product componentwise interface. The accepted pair read exposes two component rows and the displayed product ledger before any finite-data consumer receives a public projection.

The Bool sibling supplies only endpoint discrimination for the product route, while the Sum and List siblings supply branch and spine consumers after the component rows have been named. Their $\NameCert$ surfaces therefore consume already displayed product projections; they do not replace the pair by a detached sum tag, absent option row, or list spine.

Transport through $\hsame$, replay through $\Cont$, provenance through $\Pkg$, and the local $\NameCert_{\ProdUp}$ row preserve the same two projections. Hence the public $\BHist$ read is determined by the product component rows and has no independent finite-data export outside the sibling certificates.
\end{proof}
