The $\ProdUp$ finite-data dependency lattice closes over sibling routes only after the ordered-pair envelope has fixed its two component projections. Bool tag discipline from \autoref{ch:concrete-instances-bool-namecert}, Option absence and presence routing from \autoref{ch:concrete-instances-option-namecert}, Sum side tags from \autoref{ch:concrete-instances-sum-namecert}, and List finite-spine readback from \autoref{ch:concrete-instances-list-namecert} are consumed as displayed sibling rows around the product component ledger, not as detached host projections.

\begin{lemma}[Prod finite-data dependency lattice closure]
\label{lem:prod-finite-data-dependency-lattice-closure}
Every public $\ProdUp$ component projection read that cites the finite-data sibling lattice first consumes the product component ledger and then routes Bool endpoint tags, Option absent/present rows, Sum side tags, and List finite-spine readback through the corresponding sibling chapters. The route preserves the same $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ProdUp}$ row, and it exports no ambient tuple equality, unrestricted recursion principle, selected component, or detached finite-data carrier.
\end{lemma}
\begin{proof}
Begin with the product component ledger fixed by the hub children. The ledger names the left and right component projections before any sibling finite-data read is allowed to consume a tag, absence marker, side marker, or spine row.

Now read the siblings through their own chapters. Bool supplies only endpoint discrimination, Option supplies only the absent/present boundary, Sum supplies only left/right side separation, and List supplies only finite-spine readback.

The structural rows of $\ProdUp$ carry those displayed reads without changing ownership. Thus the dependency lattice closes over finite sibling data while keeping the public ordered-pair certificate inside the product NameCert surface.
\end{proof}
