\begin{theorem}[Prod option-sum sibling lattice readback]
\label{thm:prod-option-sum-sibling-lattice-readback}
Every public $\ProdUp$ ordered-pair read consumes the finite-data sibling lattice of \autoref{ch:concrete-instances-option-namecert} and \autoref{ch:concrete-instances-sum-namecert} only through the product component ledgers. The public route first reads the product componentwise interface, displayed-pair ledger, source $\NameCert$ rows, $\hsame$ transport, $\Cont$ continuation, and $\Pkg$ provenance; it then uses the option and sum sibling surfaces as finite-data consumers of those component rows.

The product pair is not a renamed option case and not a renamed sum tag. It remains the two-component ledger supplied by $\ProdUp$, and downstream finite-data consumers may read it only through the displayed component ledgers and the existing ProdUp componentwise interface.
\end{theorem}
\begin{proof}
Begin with the product componentwise interface. Theorems~\ref{thm:prod-component-history-classifier-descends-to-envelope} and~\ref{thm:prod-component-history-classifier-displayed-exactness} identify the public ordered-pair read with component histories, component classifiers, and displayed pair ledgers inside the product packet.

Next use the product finite-data sibling lattice, \autoref{thm:prod-finite-data-sibling-lattice}. It places product reads behind the finite-data lattice while keeping the ordered-pair certificate on the product carrier rows.

Now apply the option-sum component sibling route, \autoref{thm:prod-option-sum-component-sibling-route}. The option and sum chapters supply possible-absence and branch-partition consumers for already displayed component rows; they do not replace the pair ledger by an option tag or a sum branch.

Finally use the public finite-data exit package, \autoref{thm:prod-public-finite-data-exit-package}. Since every downstream finite-data read factors through the componentwise certificate, displayed-pair ledger, source certificates, $\hsame$, $\Cont$, and $\Pkg$, the sibling lattice is read back through the product component ledgers and through no host tuple equality or external projection.
\end{proof}
