\begin{theorem}[Prod finite-data real-completion sibling route]
\label{thm:prod-finite-data-real-completion-sibling-route}
Every finite product pairing used by Real and Completion consumers factors through the $\ProdUp$ public finite-data surface before any $\StreamNameUp$ or $\RegSeqRatUp$ product-window read is exported. The route first reads the product history carrier, componentwise classifier, displayed-pair ledger, source $\NameCert$ rows, $\hsame$ transport, $\Cont$ continuation, and $\Pkg$ provenance, and only then presents paired windows to \autoref{ch:concrete-instances-streamname-namecert} and regular paired coordinate reads to \autoref{ch:concrete-instances-regseqrat-namecert}.

In particular, the completion-facing product window is not a host tuple, quotient pair, selected projection, or hidden product stream. It is the displayed finite-data route of \autoref{thm:prod-finite-data-sibling-lattice}, \autoref{lem:prod-finite-data-sibling-dependency}, and \autoref{thm:prod-public-finite-data-exit-package} read before the StreamName and RegSeqRat sibling windows are consumed.
\end{theorem}
\begin{proof}
Start with the product public finite-data exit package. By \autoref{thm:prod-public-finite-data-exit-package}, a public product read exposes only the componentwise semantic certificate, displayed-pair ledger endpoints, descent to the product history envelope, source certificates, transport, continuation, and provenance rows.

The finite-data sibling route supplies the window discipline. Apply \autoref{thm:prod-finite-data-sibling-lattice} and \autoref{lem:prod-finite-data-sibling-dependency}; they keep product reads behind displayed finite sibling rows before the ordered-pair certificate is exported.

The Real and Completion consumers then read paired windows through \autoref{ch:concrete-instances-streamname-namecert} and paired regular coordinate rows through \autoref{ch:concrete-instances-regseqrat-namecert}. Since the product surface has no host tuple equality, quotient pair, selected projection, or hidden stream coordinate, the StreamName and RegSeqRat product-window reads remain downstream of $\ProdUp$.
\end{proof}

\begin{theorem}[Prod RegSeqRat and StreamName product window]
\label{thm:prod-regseqrat-streamname-product-window}
Whenever a completion-facing consumer reads a pair of stream coordinates or regular-Cauchy coordinates through $\ProdUp$, the read factors through the componentwise $\SemanticNameCert$ row, displayed-pair ledger endpoints, $\ProdHistoryClassifierUp$ descent, $\hsame$ and $\Cont$ transports, and source $\NameCert$ rows before $\StreamNameUp$ or $\RegSeqRatUp$ consumes the pair. The product window exports finite paired data only; it does not export host tuple equality, hidden projections, quotient pair representatives, or an ambient product stream.
\end{theorem}
\begin{proof}
Apply \autoref{thm:prod-finite-data-real-completion-sibling-route}. It already places Real-and-Completion product reads behind the $\ProdUp$ public finite-data surface before StreamName and RegSeqRat consumers inspect paired windows.

Specialize the downstream readers to the two completion-facing cases. A $\StreamNameUp$ product-window read consumes paired stream coordinates through the displayed product endpoint rows, while a $\RegSeqRatUp$ read consumes regular coordinate pairs through the same finite product route.

Now use consumer-row exhaustion from the public finite-data exit package. The componentwise $\SemanticNameCert$ row, displayed-pair ledger endpoints, $\ProdHistoryClassifierUp$ descent, source certificates, $\hsame$ transport, $\Cont$ continuation, and provenance rows are the whole product surface. Thus no host tuple equality, hidden projection, quotient representative, or ambient product stream remains for either downstream reader.
\end{proof}
