\begin{theorem}[Bolzano--Weierstrass bounded-sequence admission]
\label{thm:bolzano-weierstrass-bounded-sequence-admission}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet carrying the root obligation package of \autoref{thm:bolzano-weierstrass-root-obligation-package}. The bounded source row $S$ is admitted only as the source surface for the same interval-net row $K$, regular-subsequence row $R$, $\RegSeqRatUp$ readback row $Q$, and $\RealUp$ cluster seal $E$. In particular, the bounded source is read through $S,K,H,C,P,N$ before the rows $R,Q,E$ are exposed, and it cannot be replaced by a detached host sequence, an arbitrary subsequence selector, or an ambient completeness assumption.
\end{theorem}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassCarrier\_bounded\_sequence\_admission}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-namecert-obligations}. It identifies $S$ as the bounded sequence admission row and places it inside the carrier together with $K,R,Q,E,H,C,P,N$.

Apply \autoref{thm:bolzano-weierstrass-finite-subsequence-obligations} and \autoref{thm:bolzano-weierstrass-interval-net-obligation}. These force the interval-net row $K$ and the regular-subsequence row $R$ to consume the same bounded source windows rather than a second sequence source.

Finally use \autoref{thm:bolzano-weierstrass-root-obligation-package}. The structural rows $H,C,P,N$ bind the bounded source to the later readback and Real seal, so no detached host sequence or completeness principle is exported.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass regular cluster seal]
\label{thm:bolzano-weierstrass-regular-cluster-seal}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet whose bounded-sequence admission row and root obligation package are displayed. The cluster seal $E$ is regular only through the route
$$
S,K,R,Q,E,H,C,P,N .
$$
The row $R$ reads retained finite windows from $S$ through $K$, the row $Q$ reads the same windows as $\RegSeqRatUp$ data, and the row $E$ seals only that regular readback as $\RealUp$ data. No cluster seal is available from a second bounded source, a detached interval net, quotient stream equality, selected subsequence choice, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassCarrier\_regular\_cluster\_seal}
\begin{proof}
Start with bounded-sequence admission. It fixes the source row $S$ as the only bounded real-sequence surface available to the cluster route.

Use \autoref{thm:bolzano-weierstrass-regseqrat-handoff}. The handoff places the retained windows behind $K$ and $R$ before $Q$ reads them as regular rational data.

Use the interval-net obligation and the root obligation package. Together they bind $K,R,Q$ to the same support rows $H,C,P,N$.

Finally read the Real seal $E$. Since $E$ is downstream of $Q$ in the displayed route, the seal is regular by the carried readback rows and not by a host completeness or selection principle.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass closed-interval cluster export]
\label{thm:bolzano-weierstrass-closed-interval-cluster-export}
An accepted $\BolzanoWeierstrassUp$ packet exports a closed-interval cluster candidate only through the bounded-sequence admission row $S$, the closed interval net row $K$, the regular subsequence extraction row $R$, the $\RegSeqRatUp$ readback row $Q$, and the terminal $\RealUp$ seal $E$, with $H,C,P,N$ transporting, replaying, sourcing, and naming the same route. The export refuses arbitrary subsequence choice, open-cover compactness, quotient stream equality, selected least cluster points, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with bounded-source factorization and bounded-sequence admission. These rows fix $S$ as the only source of sequence data and force every cluster-facing read to pass through the displayed bounded source.

Next apply finite interval-tree induction and retained-cell monotonicity. The closed interval net row $K$ supplies the retained cells and their finite refinement route, so the packet cannot switch to an open-cover compactness proof or a detached interval net.

Use cofinal-window extraction and the regular cluster seal. The extraction row $R$ reads retained windows through $K$, the readback row $Q$ records the corresponding $\RegSeqRatUp$ data, and the seal row $E$ exports only that regular readback as $\RealUp$ cluster evidence.

Finally apply cluster-seal nonescape. The structural rows $H,C,P,N$ preserve and name the same packet, and no carrier row remains from which arbitrary subsequence choice, quotient equality, least-cluster selection, or ambient completeness could be projected.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster-seal nonescape]
\label{thm:bolzano-weierstrass-cluster-seal-nonescape}
For every accepted $\BolzanoWeierstrassUp$ packet $B=(S,K,R,Q,E,H,C,P,N)$ carrying the bounded-sequence admission and regular cluster-seal rows, any cluster-facing consumer remains inside the displayed surface
$$
S,K,R,Q,E,H,C,P,N .
$$
The consumer may read a bounded source window, a retained interval-net cell, a regular-subsequence ledger, a $\RegSeqRatUp$ readback row, and the terminal $\RealUp$ seal, but it cannot escape to an unlisted source row, an unlisted interval net, a selected least cluster point, quotient real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-bounded-sequence-admission}. It fixes $S$ and $K$ as the source and interval-net surface for the cluster route.

Apply \autoref{thm:bolzano-weierstrass-regular-cluster-seal}. It fixes $R,Q,E$ as the regular-subsequence, regular readback, and Real-seal surface downstream of those rows.

The support rows $H,C,P,N$ are the only transport, replay, provenance, and local naming coordinates in the carrier of \autoref{def:bolzano-weierstrass-carrier}. Therefore every cluster-facing read remains inside $S,K,R,Q,E,H,C,P,N$, and the refused host-level objects have no row from which they can be projected.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass retained-window refinement]
\label{thm:bolzano-weierstrass-window-retention-refinement}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet carrying the root obligation package of \autoref{thm:bolzano-weierstrass-root-obligation-package}. Every retained dyadic interval cell used by the cluster route is read through
$$
S,K,R,Q,H,C,P,N
$$
before the terminal $\RealUp$ cluster seal $E$ is exposed. The refinement preserves the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ route: no retained window may be reclassified through a new stream name, a detached dyadic grid, a second rational-readback package, or a host compactness selector.
\end{theorem}
\begin{proof}
Start with the root interval-tree obligation. It displays the retained dyadic cells through $S$ and $K$, so each retained window is already attached to the bounded source and interval-net rows before the extraction route is read.

Next apply the root subsequence extraction obligation. The row $R$ consumes only those retained cells, and the $\StreamNameUp$ and $\DyadicRatCoreUp$ data used by the extraction remain the ones displayed by the same source and interval-net package.

Now use the RegSeqRat cluster package. The readback row $Q$ is the $\RegSeqRatUp$ route for the retained windows already carried by $S,K,R$, so it cannot introduce a second rational-readback surface or a detached dyadic grid.

Finally apply the root Real-seal obligation and the root obligation package. The cluster seal $E$ is downstream of $S,K,R,Q,H,C,P,N$, while $H,C,P,N$ transport, replay, record provenance, and name the same route. Hence the retained-window induction is preserved all the way to the $\RealUp$ seal without importing a new stream, grid, readback package, or host selector.
\end{proof}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassCarrier\_window\_retention\_refinement}
