\chapter{Computation as Continuation: BEDC's Operational Semantics}
\label{ch:capstones-computation-as-continuation}

The continuation primitive $\Cont$ of \autoref{ch:core-relational-extension-and-continuation} carries the formal content of a small-step transition relation. Reading $\Cont\,h\,m\,h'$ as ``the history $h$ steps via mark $m$ to history $h'$'' makes $\Cont$ a Plotkin-style structural operational semantics over the BEDC primitive layer. The chapter records the structural isomorphism between $\Cont$ and the small-step relations of standard programming-language semantics, and locates termination, big-step semantics, and behavioural equivalence as classifier-level notions already present in the kernel.

\section{Continuation as small-step transition}
\label{sec:computation-as-continuation-small-step}

\begin{theorem}[Continuation-SOS correspondence]
\label{thm:computation-as-continuation-correspondence}
For every closed inductive program syntax $S$ equipped with a Plotkin-style small-step relation $\to_{S}$, there exists a naming certificate over $S$ whose continuation is naturally isomorphic to $\to_{S}$. Termination of $\to_{S}$ corresponds to the well-foundedness of the certificate's continuation chain; big-step semantics arises as the classifier closure of the continuation; behavioural equivalence is $\hsame$ on the underlying history carrier.
\leanstmt{BEDC.Reflection.computation\_as\_continuation\_correspondence}
\end{theorem}

\paragraph{Capstone.}
The same continuation ledger has three concrete readings: as categorical
hom-carrier data, as a unary prefix preorder witness, and as monoid append of
continuation tails.

\begin{theorem}[Unary prefix category correspondence]
\label{thm:unary-prefix-preorder-category-correspondence}
For unary histories $a,b,f$, the displayed ledger
$\mathsf{CategoryHomCarrier}(a,b,f)$ is exactly the datum that $f$ is the
unary continuation tail witnessing the concrete prefix comparison from $a$ to
$b$: $\mathsf{UnaryHistory}(a)$, $\mathsf{UnaryHistory}(f)$, and
$\ContR(a,f,b)$. Under this correspondence, $\emp$ is the identity tail,
categorical composition is BEDC monoid append of tails, and
$\mathsf{PreorderPrefixLE}$ transitivity is composition closure up to
$\hsame$.
\end{theorem}
\begin{proof}
Unfold $\mathsf{CategoryHomCarrier}$. A hom-carrier ledger already contains
the unary source and morphism witnesses together with the continuation
$\ContR(a,f,b)$, so the prefix witness is obtained by reading $f$ as the
displayed tail from $a$ to $b$.

Conversely, the prefix tail data supplies the source and morphism witnesses
directly, and unary continuation closure supplies the target witness. The
continuation field is the displayed $\ContR(a,f,b)$, so the hom-carrier ledger
is rebuilt. The concrete preorder form is the same tail display, with
\autoref{thm:preorder-prefix-append-unary-tail} giving the canonical append
presentation.

The identity case is \autoref{thm:category-hom-carrier-empty-identity}: the
empty tail witnesses the identity continuation at every unary object.
Composition uses \autoref{thm:category-hom-carrier-comp-closed}, while the
preorder side uses \autoref{thm:preorder-prefix-transitivity}. The agreement
of these two composites is the unit and associativity content of
\autoref{thm:history-continuation-monoid-laws}, with comparison of resulting
tails taken through $\hsame$.
\end{proof}
