\chapter{Inter-Hist Locality: From No God's-Eye View to Light-Speed Constancy}
\label{ch:capstones-inter-hist-locality}

This capstone is the road-map sibling to \autoref{ch:capstones-observer-hist-identity}. Where that chapter formalizes the SINGLE-Hist commitments that BEDC already proves --- namely that an observer is identified with the Hist of its observations, with no observer-substance carrier behind the record --- the present chapter scaffolds the MULTI-Hist consequences that BEDC must develop next. When several independent Hist values are considered together, with no shared base and no shared time-step indexing, the kernel does not give a global frame and cannot give one without violating the closed-inductive structure of \(\Hist\). In that setting only inter-Hist invariants can carry frame-independent physical content, and the maximum cross-Hist causal rate, in particular, must be observer-symmetric and constant across all observers in a configuration. That last consequence is the structural skeleton of the constancy of light speed in special relativity. The chapter catalogues the structure: multi-Hist configuration, no global synchronization, inter-Hist relation, observer-symmetric invariant, maximum cross-Hist causal rate, and the observer-independence of that maximum. Most of the multi-Hist semantics is currently a SCHEMA-ONLY HORIZON in BEDC: the type signatures and statement targets are sketched here, and the closed witnesses are deferred to a future BEDC physics-of-multi-observer development that does not yet exist. The chapter is therefore a roadmap, not a proof; it identifies the interface that future BEDC chapters would close. The structural commitments of the capstone connect to existing relational physics traditions: Rovelli's relational quantum mechanics, Wheeler's ``It from Bit'', Connes's noncommutative geometry, and Penrose's spin networks all locate physical content in observer-relations rather than in a privileged global frame. BEDC differs from these traditions in that it constructs the relational substrate from a still more primitive layer: distinction (\(\Hist\)) and observation (\(\Cont\)). The chapter falls under the same axiom-purity gate as the rest of the project --- whether multi-Hist semantics can preserve no-\(\mathsf{Classical.choice}\) / no-\(\mathsf{Quot.sound}\) / no-\(\mathsf{propext}\) is itself part of the road-map question, and is articulated as such in the closing section.

\section{Multi-Hist configurations}
\label{sec:multi-hist-config}

\begin{definition}[Multi-Hist configuration]
\label{def:multi-hist-config}
A multi-Hist configuration is a finite collection of Hist values \(h_1, \ldots, h_n\) considered together, with no requirement of a shared base history and no requirement of a shared time-step indexing. The configuration is the bare collection: the kernel does not append, glue, or synchronize the members.
\end{definition}
\begin{definition}[No global synchronization]
\label{def:no-global-sync}
There is no Hist-valued global synchronization for multi-Hist configurations: there is no \(\Hist\) value \(h_g\) such that for every multi-Hist configuration, \(h_g\) records a privileged shared ``now'' across all members of the configuration. The closed-inductive structure of \(\Hist\) does not admit such an \(h_g\).
\end{definition}
\begin{theorem}[Hists are frame-independent]
\label{thm:hists-frame-independent}
For any two \(\Hist\) values \(h_a, h_b\), neither carries the other's time-step indexing intrinsically. Any cross-Hist temporal correlation must be constructed via an external relation, not read off either Hist alone, and any such relation is itself a Hist-level construction subject to the same no-global-frame constraint.
\end{theorem}
\begin{lemma}[Empty configuration is degenerate]
\label{lem:empty-config-degenerate}
A multi-Hist configuration with zero or one members carries no inter-Hist content. The smallest non-degenerate configuration has two members, and the smallest configuration in which cross-Hist causal dependence (\autoref{def:cross-hist-causal-schema}) can be non-trivial likewise has two members.
\end{lemma}
\begin{lemma}[Configuration extension preserves no-global-sync]
\label{lem:extension-preserves-no-sync}
Adding a new \(\Hist\) value to an existing multi-Hist configuration does not produce a global synchronization that the original configuration lacked. No-global-synchronization is monotone: it is preserved under configuration extension, and cannot be acquired by accumulating Hists.
\end{lemma}
\begin{remark}[Reading: no observer-of-observers]
\label{rem:no-gods-eye}
This section formalizes the no-God's-eye-view commitment. There is no observer-of-observers that synchronizes the multi-Hist totality, because the kernel is silent about a global frame and the closed-inductive \(\Hist\) type does not admit one. By the sibling capstone (\autoref{ch:capstones-observer-hist-identity}), once observer is identified with Hist, no super-observer can coexist: any candidate super-observer is itself a Hist, and is subject to the same locality constraints as every other member of a configuration. \autoref{lem:extension-preserves-no-sync} shows that the absence cannot be repaired from inside the kernel by adding more observers; it is a feature of the closed-inductive structure of \(\Hist\) rather than a contingent fact about the current configuration.
\end{remark}

\section{Inter-Hist invariants}
\label{sec:inter-hist-invariants}

\begin{definition}[Inter-Hist relation]
\label{def:inter-hist-relation}
An inter-Hist relation is a predicate \(R(h_a, h_b)\) on pairs of \(\Hist\) values that is observer-symmetric: \(R(h_a, h_b)\) holds if and only if \(R(h_b, h_a)\) holds, up to \(\hsame\) on each component. Symmetry is required at the type-signature level: the predicate cannot privilege one slot over the other.
\end{definition}
\begin{definition}[Inter-Hist invariant]
\label{def:inter-hist-invariant}
An inter-Hist invariant is a function \(I : \Hist \times \Hist \to \Unary\) that is observer-symmetric and frame-independent: for any pair of perspectives on the configuration --- that is, for either \(\Hist\) taking the role of measurement-anchor --- the function \(I\) produces the same output up to \(\hsame\), and the output does not depend on any external choice of frame.
\end{definition}
\begin{theorem}[Invariants are observer-independent]
\label{thm:invariants-observer-independent}
Every inter-Hist invariant produces the same value regardless of which \(\Hist\) is taken as the perspective anchor. The value is a property of the pair as such, and not of either individual \(\Hist\); it is not measurable from inside one observer's record except as a relational quantity involving the other.
\end{theorem}
\begin{proposition}[Invariants compose under \(\hsame\)]
\label{prop:invariants-hsame-stable}
If \(I\) is an inter-Hist invariant and \(h_a \hsame h_a'\) and \(h_b \hsame h_b'\), then \(I(h_a, h_b) \hsame I(h_a', h_b')\). The invariant respects the kernel's history-equivalence relation; it cannot distinguish histories that the kernel does not distinguish.
\end{proposition}
\begin{lemma}[Trivial invariants exist]
\label{lem:trivial-invariants-exist}
The constant function \(I(h_a, h_b) := \emp\) and the constant function \(I(h_a, h_b) := \UnaryHistory\) are inter-Hist invariants in the sense of \autoref{def:inter-hist-invariant}. The class of inter-Hist invariants is therefore non-empty before any physics is committed; the substantive content of the road-map is the construction of non-trivial invariants whose values discriminate between configurations.
\end{lemma}
\begin{proposition}[\(\psame\)-stability of invariants]
\label{prop:psame-stable}
If \(I\) is an inter-Hist invariant and \(p_a \psame p_a'\) is a probe-equivalence at the anchor of \(h_a\) and \(p_b \psame p_b'\) at the anchor of \(h_b\), the invariant \(I\) returns \(\hsame\)-equivalent values on the corresponding pairs. Inter-Hist invariants are stable under both kernel-level history equivalence (\autoref{prop:invariants-hsame-stable}) and kernel-level probe equivalence; they cannot distinguish what the kernel does not distinguish at either layer.
\end{proposition}
\begin{remark}[Reading: relational content is forced]
\label{rem:relational-content}
This section formalizes the operationalist principle that, in the absence of a privileged frame, all physical content lives in inter-observer relations rather than in any one observer's record. The principle is forced by no-global-synchronization (\autoref{def:no-global-sync}); it is not assumed. In particular, an observer's individual Hist is not a frame-independent carrier of physical content on its own; only \(I\)-images of pairs are. \autoref{prop:psame-stable} sharpens this: invariants cannot smuggle in distinctions below the kernel's resolution, on either the history or the probe layer, so the relational content lives strictly in the kernel-level equivalence quotient.
\end{remark}

\section{Cross-Hist causal dependence (schema-only)}
\label{sec:cross-hist-causal}

\begin{definition}[Cross-Hist causal dependence --- SCHEMA-ONLY]
\label{def:cross-hist-causal-schema}
A cross-Hist causal dependence is a relation \(C(h_a, h_b, k)\) saying ``\(h_b\)'s most recent \(k\) \(\Cont\) steps depend on \(h_a\)'s recent steps''. The relation is currently a SCHEMA-ONLY HORIZON in BEDC: the kernel exposes the type signature, but no closed witness produces a non-trivial cross-Hist causal relation. Future BEDC chapters on multi-Hist physics would close this schema by giving a constructive predicate together with concrete witnesses.
\end{definition}
\begin{definition}[Maximum cross-Hist causal rate --- SCHEMA-ONLY]
\label{def:max-causal-rate-schema}
The maximum cross-Hist causal rate is a unary-valued function \(\mathsf{MaxRate}\) on multi-Hist configurations such that, for every cross-Hist causal dependence \(C(h_a, h_b, k)\), the ratio of cross-affected \(\Cont\) steps in \(h_b\) to corresponding \(\Cont\) steps in \(h_a\) is bounded above by \(\mathsf{MaxRate}\). SCHEMA-ONLY: the upper-bound theorem awaits the multi-Hist semantics that gives \(C\) its closed witnesses.
\end{definition}
\begin{theorem}[Maximum rate is an inter-Hist invariant --- SCHEMA-ONLY]
\label{thm:max-rate-invariant-schema}
The maximum cross-Hist causal rate, when defined, is an inter-Hist invariant in the sense of \autoref{def:inter-hist-invariant}: its value is observer-symmetric and frame-independent. SCHEMA-ONLY: this theorem is part of the road-map; its closed proof requires the multi-Hist causal-dependence semantics to be made constructive.
\end{theorem}
\begin{theorem}[Maximum rate is an observer-independent constant --- SCHEMA-ONLY]
\label{thm:max-rate-constant-schema}
For any multi-Hist configuration with a non-trivial cross-Hist causal dependence, the maximum cross-Hist causal rate is the same constant for all observers in the configuration. Equivalently, no observer can measure a different value for the maximum rate without invoking a privileged frame; and no privileged frame exists, by \autoref{def:no-global-sync}.
\end{theorem}
\begin{corollary}[Light-speed-like constant]
\label{cor:light-speed-constant-schema}
A multi-Hist configuration that admits a non-trivial cross-Hist causal dependence has a single observer-independent maximum-rate constant attached to it. The form of the result --- ``a constant maximum cross-Hist causal rate exists and is observer-independent'' --- is the structural skeleton of the constancy of light speed in special relativity. The empirical specific value of the constant is not derived inside BEDC; only the form is.
\end{corollary}
\begin{lemma}[Causal dependence is asymmetric in the time slot --- SCHEMA-ONLY]
\label{lem:causal-asymmetric-time-schema}
The relation \(C(h_a, h_b, k)\) of \autoref{def:cross-hist-causal-schema} is asymmetric in the time slot \(k\): \(C(h_a, h_b, k)\) and \(C(h_b, h_a, k)\) are distinct predicates in general, even though the inter-Hist invariants of \autoref{sec:inter-hist-invariants} are observer-symmetric. The asymmetry is the content of ``\(h_b\) depends on \(h_a\)'' as opposed to ``\(h_a\) depends on \(h_b\)'', and is exactly the structure that the maximum-rate constant must average over to recover observer symmetry.
\end{lemma}
\begin{lemma}[Causal dependence respects \(\hsame\) --- SCHEMA-ONLY]
\label{lem:causal-hsame-schema}
If \(C(h_a, h_b, k)\) and \(h_a \hsame h_a'\) and \(h_b \hsame h_b'\), then \(C(h_a', h_b', k)\). The cross-Hist causal-dependence predicate is required to be \(\hsame\)-stable; without this stability, no inter-Hist invariant could be defined on top of it without leaking kernel-undistinguishable distinctions.
\end{lemma}
\begin{proposition}[Triviality at degenerate configurations --- SCHEMA-ONLY]
\label{prop:max-rate-trivial-schema}
For a multi-Hist configuration with no non-trivial cross-Hist causal dependence, the maximum cross-Hist causal rate is the trivial bound, and \autoref{thm:max-rate-constant-schema} reduces to a vacuous truth. The non-trivial content of the maximum-rate constant arises only once \(C\) has at least one closed witness on the configuration; until then, the road-map cannot distinguish the constant numerically.
\end{proposition}
\begin{remark}[Reading: the structural argument]
\label{rem:light-speed-like}
The structural argument runs as follows. No-God's-eye view (\autoref{def:no-global-sync}) forces all physical content into inter-Hist invariants (\autoref{thm:invariants-observer-independent}); the maximum cross-Hist causal rate is one such invariant (\autoref{def:max-causal-rate-schema}); the symmetry of ``no privileged frame'' forces this rate to be the same constant for all observers (\autoref{thm:max-rate-constant-schema}). Each step is inevitability under the previous, not a separate postulate. In standard relativistic terms: BEDC derives the form of an invariant maximum signal speed from no-global-frame plus relational content; what it does not derive is that this constant takes any particular numerical value.
\end{remark}

\section{Roadmap toward physics}
\label{sec:roadmap-toward-physics}

\begin{remark}[Form of the next dependency chain]
\label{rem:next-dependency-chain}
The capstone identifies the next BEDC roadmap, parallel in form to the Riemann Hypothesis dependency chain (\autoref{ch:capstones-riemann-hypothesis}). It is a sequence of multi-Hist namecert chapters that close the schema-only horizons of \autoref{sec:cross-hist-causal}. The chain proceeds: (i) \(\NameCert\) for \(\mathsf{MultiHistConfig}\); (ii) \(\NameCert\) for \(\mathsf{CrossHistCausal}\); (iii) \(\NameCert\) for \(\mathsf{MaxCausalRate}\); (iv) Lorentz-geometry \(\NameCert\), in which the inter-Hist invariant produces a Minkowski-like distance from the observer-symmetric maximum rate; (v) curved spacetime as a Lorentz-\(\NameCert\) with non-trivial gluing data over a multi-Hist configuration; (vi) quantum-state \(\NameCert\) as multi-Hist superposition, in which the relational content is carried by \(\Eone\)/\(\Ezero\) refinements rather than by metric data; and so on. Each step on this chain is its own chapter and its own statement-only Lean target.
\end{remark}

\begin{remark}[Falsification surfaces along the chain]
\label{rem:falsification-surfaces}
Each step of \autoref{rem:next-dependency-chain} carries its own falsification surface. Step (i) fails if no closed witness for \(\mathsf{MultiHistConfig}\) can be produced without smuggling in a global frame. Step (ii) fails if cross-Hist causal dependence cannot be expressed as an \(\hsame\)- and \(\psame\)-stable predicate. Step (iii) fails if the maximum-rate function cannot be defined without choice. Step (iv) fails if the candidate Minkowski-like distance is not symmetric in the two observers, or if it does not respect \autoref{prop:invariants-hsame-stable}. Step (v) fails if the gluing data over the configuration cannot be made constructive. Step (vi) fails if the multi-Hist superposition predicate forces \(\mathsf{propext}\). The road-map's intermediate failures are themselves informative; they are not engineering setbacks but structural results about where distinction-foundationalism stops being sufficient.
\end{remark}

\begin{remark}[Relation to existing single-Hist Lean targets]
\label{rem:relation-existing-lean}
The Lean targets named in \autoref{def:multi-hist-config} through \autoref{prop:max-rate-trivial-schema} are statement-only and do not yet have closed proofs. They are nevertheless not isolated from the rest of the formalization. \(\mathsf{InterHistInvariant}\) (\autoref{def:inter-hist-invariant}) takes \(\Hist\)-pairs to \(\Unary\), and \(\Unary\) is already a closed-inductive carrier in BEDC; \(\mathsf{MaxCausalRate}\) (\autoref{def:max-causal-rate-schema}) is unary-valued in the same sense. The interface uses no Lean fragment that BEDC has not already committed to. What it adds is the multi-Hist combinator structure: pairing two \(\Hist\) values into a configuration, and predicating over pairs.
\end{remark}

\begin{remark}[Connection to relational physics traditions]
\label{rem:relational-physics}
The structural commitments of this capstone are the same commitments as Rovelli's relational quantum mechanics, Wheeler's ``It from Bit'', Connes's noncommutative geometry, and Penrose's spin networks: physical content is observer-relational, not located in any single observer's record, and observer is not a substance prior to its observations. BEDC differs from these traditions in that it constructs the relational substrate from a still more primitive layer: distinction (\(\Hist\)) and observation (\(\Cont\)), with no observer-substance carrier behind either, and with everything closed-inductive. Where those traditions take observer-relations as physical primitives, BEDC derives them from the structure of distinction.
\end{remark}

\begin{remark}[Schema-only horizons and axiom-purity]
\label{rem:schema-only-axiom-purity}
A central open question on this roadmap is whether the multi-Hist semantics can be closed inside BEDC's axiom-purity gate. If yes, BEDC's distinction-foundationalist position extends from pure mathematics into physics with no additional axiomatic cost: the same fragment that proves the single-Hist commitments of \autoref{ch:capstones-observer-hist-identity} would also prove the multi-Hist commitments of this chapter. If no, the boundary point at which axiom-purity fails would itself be a structurally meaningful result: it would mark precisely where physics requires more than distinction --- whether choice, propositional extensionality, or quotient sound is the first to be needed, and on which specific schema. Either outcome is informative.
\end{remark}

\begin{remark}[Why the chain is acyclic]
\label{rem:chain-acyclic}
The dependency chain of \autoref{rem:next-dependency-chain} is acyclic by construction. Step (i) \(\mathsf{MultiHistConfig}\) does not depend on cross-Hist causal dependence, only on \(\Hist\); step (ii) builds \(\mathsf{CrossHistCausal}\) on top of (i); step (iii) extracts a single unary upper bound from (ii); steps (iv) and (v) elaborate that bound into geometric data; step (vi) lifts the same machinery to a \(\NameCert\) over multi-Hist superpositions. Each step strictly extends the predicate vocabulary of the previous step. The order in which the multi-Hist semantics must be assembled is exactly the order of the chain; no step can be deferred past a later step without circularity.
\end{remark}

\begin{remark}[\(\Eone\)/\(\Ezero\) refinements at the multi-Hist level]
\label{rem:e1-e0-multi-hist}
The single-Hist semantics distinguishes \(\Eone\) (extensional, observation-driven) from \(\Ezero\) (intensional, name-driven) at the level of one observer's record. The multi-Hist roadmap inherits this distinction: an inter-Hist invariant may be sensitive to \(\Eone\)-level refinements of the two component records, to \(\Ezero\)-level refinements, or to both. Quantum-state \(\NameCert\)s in step (vi) of \autoref{rem:next-dependency-chain} are expected to live in the \(\Eone\)-sensitive class, and metric \(\NameCert\)s in steps (iv) and (v) in the \(\Ezero\)-sensitive class. Articulating which refinement layer carries which physical content is part of the multi-Hist development.
\end{remark}

\begin{remark}[Single-Hist obligations as preconditions]
\label{rem:single-hist-preconditions}
The roadmap of this capstone presupposes the single-Hist obligations articulated in the sibling capstone (\autoref{ch:capstones-observer-hist-identity}). Without observer-Hist identity, the multi-Hist configuration of \autoref{def:multi-hist-config} would not yet be a configuration of observers; without \(\hsame\)-stability of single-observer content, \autoref{prop:invariants-hsame-stable} would not type-check at the inter-observer level. The two capstones close adjacent layers of the same problem.
\end{remark}

\section{Closing}
\label{sec:closing-inter-hist}

\begin{remark}[What this capstone is and is not]
\label{rem:what-this-is-not}
This capstone is not a derivation of relativity, of quantum mechanics, or of any particular physical theory. It is a derivation of the form of an observer-independent maximum-rate constant from the combination of distinction-foundationalist commitments (single-Hist identification of observer with record, no observer-substance carrier) and the closed-inductive structure of \(\Hist\). The form is the strong claim; the value is not derived. Equally, the capstone is not a claim that BEDC will succeed in closing the multi-Hist roadmap inside its axiom-purity gate. It is a claim that the question is well-posed and that the interface is now sketched precisely enough that progress and failure can be told apart.
\end{remark}

\begin{remark}[The structure of physics from observer locality]
\label{rem:closing-physics-from-locality}
The capstone makes one structural argument. In a configuration of independent Hists with no global frame, all physical content lives in observer-symmetric inter-Hist invariants, and the maximum cross-Hist causal rate must be observer-independent. This is the BEDC-derived skeleton of the relativistic structure of physics. The current chapter does not produce that physics; it identifies the interface that a future BEDC physics chain would close. Whether closure is possible inside the axiom-purity gate is the next research question. The chapter falls under the project's axiom-purity gate, and the road-map question of whether physics can be constructively closed inside that gate is itself open. \autoref{rem:falsification-surfaces} catalogues the specific surfaces along which the road-map can fail informatively; the answer to the road-map question will be assembled from a sequence of step-by-step constructive successes or step-localized failures, not declared in advance.
\end{remark}
