\begin{theorem}[Real RegSeqRat terminal budget exhaustion]
\label{thm:real-regseqrat-terminal-budget-exhaustion}
Let $Q$ be an accepted $\RegSeqRatUp$ packet and let $S$ be a finite RegSeqRat request accepted by the $\RealUp$ seal over $Q$. A terminal-budget consumer of $S$ is accepted exactly when its visible rows factor through the ordered four-face packet
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The packet consists of the $\DyadicRatCoreUp$ endpoint, radius, and distance ledgers; the $\StreamNameUp$ finite schedules; the $\RegSeqRatUp$ regularity, classifier, and provenance rows; and the local $\RealUp$ terminal seal row, all transported by the displayed $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ coordinates.

Conversely, any packet with exactly these four faces and exactly these support rows repacks as the accepted $\RealUp$ terminal-budget read of $S$. The exhaustion exports no quotient stream equality, host real equality, selected limit, countable-choice selector, ambient completeness principle, arithmetic package, order package, or metric-completeness row.
\end{theorem}
\begin{proof}
For the forward direction, begin with an accepted terminal-budget consumer of the finite RegSeqRat request. Apply \autoref{thm:regseqrat-finite-request-terminal-budget-factorization} to place the request on its finite terminal-budget section, with the RegSeqRat classifier, regularity, readback, and provenance rows already tied to a finite source packet.

Next apply \autoref{thm:real-regseqrat-finite-request-fusion-selector-budget-lock}. The $\RealUp$ seal over the accepted RegSeqRat packet must reuse the same finite request section, so the StreamName schedule, DyadicRatCore endpoint, radius, and distance ledgers, RegSeqRat rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\RealUp}$ row cannot be replaced by a second terminal-budget surface.

Now use \autoref{thm:real-l10-four-face-exactness}. It identifies the visible rows of the accepted terminal $\RealUp$ read with the finite four-face packet over DyadicRatCore, StreamName, RegSeqRat, and the local Real seal. Thus the terminal-budget consumer has no visible coordinate outside the ordered packet in the statement.

For the reverse direction, suppose the displayed DyadicRatCore ledgers, StreamName schedules, RegSeqRat regularity and classifier rows, and local $\RealUp$ terminal seal row are already present with the listed support coordinates. Apply \autoref{thm:real-l10-terminal-four-face-correspondence} to repack those rows as the terminal $\RealUp$ read.

It remains to match that terminal read with the original finite request. The finite-request factorization and selector-budget lock identify the RegSeqRat source section and the $\RealUp$ seal section as the same packet, so the repacked four-face read is exactly the accepted terminal-budget read of $S$. Since the cited routes do not export quotient stream equality, host real equality, selected limits, countable-choice selectors, ambient completeness, arithmetic or order packages, or metric-completeness rows, none of those data are available through this exhaustion.
\end{proof}

\begin{theorem}[Real RegSeqRat terminal budget seal uniqueness]
\label{thm:real-regseqrat-terminal-budget-seal-uniqueness}
Let $Q$ be an accepted $\RegSeqRatUp$ packet and let $S$ be a finite RegSeqRat request accepted by the $\RealUp$ seal over $Q$. Suppose two accepted terminal-budget reads of $S$ display the same $\DyadicRatCoreUp$ endpoint, radius, and distance ledgers, the same $\StreamNameUp$ finite schedules, the same $\RegSeqRatUp$ regularity, classifier, and provenance rows, the same local $\RealUp$ seal row, and the same displayed $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ support rows.

Then the two public finite $\RealUp$ seal rows coincide. This equality is only the equality of the visible terminal-budget seal row; it does not assert quotient stream equality, host real equality, selected limits, countable-choice selectors, ambient completeness, arithmetic or order packages, metric-completeness rows, standard bridge rows, or any equality of hidden completion carriers.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-regseqrat-terminal-budget-exhaustion} to each accepted terminal-budget read. Both reads factor through the ordered four-face packet
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The hypotheses identify every displayed face of these two packets: the dyadic endpoint, radius, and distance ledgers, the StreamName schedules, the RegSeqRat regularity, classifier, and provenance rows, and the local Real seal row. They also identify the support rows $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$.

Next use \autoref{thm:real-l10-terminal-source-lock} and \autoref{thm:real-l10-terminal-four-face-correspondence}. The source lock keeps both terminal reads on the same L10 source route, while the four-face correspondence reads the identified packet as the terminal $\RealUp$ seal read. Thus neither read can obtain a second terminal source after the four visible faces and support rows have been fixed.

It remains to check that both reads are attached to the same finite request section. Apply \autoref{thm:regseqrat-finite-request-terminal-budget-factorization} to the RegSeqRat request and \autoref{thm:real-regseqrat-finite-request-fusion-selector-budget-lock} to the Real seal over it. These two locks identify the RegSeqRat source section and the Real selector-budget section as the same terminal-budget packet for $S$.

Finally invoke \autoref{thm:streamname-real-completion-four-object-exit-route} and \autoref{thm:streamname-open-phase-four-face-terminality}. The exit route names the same four public objects, and terminality says that agreement on those objects and the displayed support rows determines a single terminal finite route. Hence the visible public $\RealUp$ seal row of the first read is the visible public $\RealUp$ seal row of the second read.

All equalities used above are equalities of the finite displayed packet. The cited routes export no quotient stream equality, host real equality, selected limit, countable-choice selector, ambient completeness, arithmetic or order package, metric-completeness row, standard bridge row, or hidden completion carrier, so the uniqueness conclusion has exactly the public finite seal-row scope stated above.
\end{proof}

\begin{theorem}[Real RegSeqRat terminal budget four-face naturality]
\label{thm:real-regseqrat-terminal-budget-four-face-naturality}
Let $Q$ be an accepted $\RegSeqRatUp$ packet and let $S$ be a finite RegSeqRat request accepted by the $\RealUp$ seal over $Q$. Suppose an accepted terminal-budget read of $S$ is transported through the displayed $\BHist$, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ support rows, while preserving the $\DyadicRatCoreUp$ endpoint, radius, and distance ledgers, the $\StreamNameUp$ finite schedules, the $\RegSeqRatUp$ regularity, classifier, and provenance rows, and the local $\RealUp$ seal row.

Then the transported read has the same public $\RealUp$ terminal-budget seal row as the original read, and it is the same four-face read through
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The transported read exports no quotient stream equality, selected limit, choice selector, ambient completeness, arithmetic or order package, metric-completeness row, standard bridge row, or hidden completion carrier.
\end{theorem}
\begin{proof}
Apply terminal-budget exhaustion to the original read. The accepted read is exhausted by the four displayed faces, together with the DyadicRatCore ledgers, StreamName schedules, RegSeqRat rows, local Real seal row, and the listed support rows.

Apply the same exhaustion theorem to the transported read. The transport hypotheses preserve exactly those visible rows and support coordinates, so the transported read factors through the same ordered four-face packet and has no additional terminal-budget coordinate.

Now use terminal-budget seal uniqueness. Since the two accepted reads display the same dyadic, schedule, regularity, classifier, provenance, Real seal, transport, continuation, package, and naming rows, their public finite $\RealUp$ seal rows coincide.

The non-escape conclusion is inherited from the two preceding results. Exhaustion supplies no hidden completion data, and uniqueness identifies only the visible finite seal row, so the transported read cannot export quotient stream equality, selected limits, choice selectors, ambient completeness, arithmetic or order packages, metric-completeness rows, standard bridge rows, or hidden completion carriers.
\end{proof}

\begin{theorem}[Real terminal-budget pasting exactness]
\label{thm:real-terminal-budget-pasting-exactness}
Let $Q$ be an accepted $\RegSeqRatUp$ packet under a fixed $\RealUp$ seal, and
let $S_0$ and $S_1$ be accepted finite RegSeqRat requests with an accepted
overlap $S_{01}$. Suppose their terminal-budget reads agree on $S_{01}$ in the
$\DyadicRatCoreUp$ endpoint, radius, and distance ledgers, the $\StreamNameUp$
finite schedules, the $\RegSeqRatUp$ regularity, classifier, and provenance
rows, the local $\RealUp$ seal row, and the displayed $\BHist$,
componentwise $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ support rows.
Then the pasted terminal-budget read has the same public $\RealUp$ seal row as
the two restrictions on the overlap and factors through the same ordered
four-face route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$

The pasted read exports no quotient stream equality, host real equality,
selected limit, countable-choice selector, ambient completeness principle,
arithmetic package, order package, metric-completeness row, standard bridge
row, or hidden completion carrier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-regseqrat-terminal-budget-exhaustion} to the two
accepted reads. Each restriction is exhausted by the DyadicRatCore endpoint,
radius, and distance ledgers, the StreamName schedules, the RegSeqRat
regularity, classifier, and provenance rows, the local Real seal row, and the
displayed support rows.

On the overlap $S_{01}$, use
\autoref{thm:real-regseqrat-terminal-budget-seal-uniqueness}. The agreement
hypotheses identify every visible terminal-budget row, so the public
$\RealUp$ seal row is single on the overlap.

Paste the two terminal-budget reads along this common seal row. The pasted
read has exactly the displayed dyadic, StreamName, RegSeqRat, Real seal, and
support coordinates inherited from its restrictions, with no extra terminal
coordinate at the gluing boundary.

Finally apply
\autoref{thm:real-regseqrat-terminal-budget-four-face-naturality}. Naturality
transports the pasted read along the same support rows and keeps it on the
ordered four-face route. The non-escape clauses are inherited from exhaustion,
seal uniqueness, and naturality, so the pasted terminal-budget read does not
claim quotient, host-real, selected-limit, choice, completeness, arithmetic,
order, metric-completion, bridge, or hidden-completion data.
\end{proof}
