\begin{theorem}[RealAlgOrder MetricSpace SOne positive boundary]
\label{thm:realalgorder-metricspace-sone-positive-boundary}
For constant rational real names, any $\RealAlgOrderUp$ apartness packet that is
consumed simultaneously by $\MetricSpaceUp$ and by $\SOneUp$ factors through one
shared positive-boundary package. The package consists exactly of the common
rational endpoint witnesses, their $\RealUp$ constant names, the
$\RealAlgOrderUp$ apartness and positive-gap rows, the $\MetricSpaceUp$
positive-distance row, the $\SOneUp$ component product and unit-equation rows,
the displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the
local $\NameCert$ rows.

The package supplies no trichotomy row, quotient equality, host metric
structure, compactness, connectedness, or Real completeness datum.
\end{theorem}
\begin{proof}
Begin with
\autoref{thm:realalgorder-constant-rational-scoped-certificate}. It fixes the
constant-rational endpoints as rational witnesses transported through the
$\RealUp$ e-one boundary, and it displays the carrier, classifier, order,
apartness, $\hsame$, $\Cont$, $\Pkg$, and local naming rows available to the
$\RealAlgOrderUp$ packet.

Next apply
\autoref{thm:realalgorder-metricspace-public-positive-distance-handoff}. The
apartness or positive-gap row is repacked as the $\MetricSpaceUp$
positive-distance component without changing the endpoints, transports,
continuation routes, provenance, or local certificate.

Use \autoref{thm:realalgorder-sone-unit-equation-apartness-boundary} for the
circle-side consumer. The $\SOneUp$ row reads the same real component endpoints,
the product carrier, the unit-equation witness, componentwise classifier rows,
and equation transports; it does not introduce an angle quotient or an
independent equality surface.

Finally compare the two consumer reads with
\autoref{thm:realalgorder-metric-sone-public-interface-triad} and
\autoref{thm:metricspace-public-law-package}. The shared row set is exactly the
displayed endpoint, positive-distance, product, unit-equation, transport,
continuation, provenance, and local certificate package, so no trichotomy,
quotient equality, host metric structure, compactness, connectedness, or Real
completeness coordinate is present.
\end{proof}

\begin{theorem}[RealAlgOrder constant apartness SOne unit boundary]
\label{thm:realalgorder-constant-apartness-sone-unit-boundary}
For constant rational real names feeding an accepted $\SOneUp$
component-and-unit-equation consumer, the $\RealAlgOrderUp$ apartness boundary
used by that consumer is exactly the constant-rational positive-boundary
package of \autoref{thm:realalgorder-metricspace-sone-positive-boundary}. It
contains the two displayed real component rows, the product carrier, the
unit-equation witness, the positive-distance handoff through $\MetricSpaceUp$,
the $\hsame$ and $\Cont$ transport rows, the $\Pkg$ provenance row, and the
local $\NameCert$ rows.

It does not supply an angle quotient, completed-real equality, trichotomy,
host metric structure, compactness, connectedness, or Real completeness.
\end{theorem}
\begin{proof}
Project the accepted circle consumer through
\autoref{thm:realalgorder-sone-unit-equation-apartness-boundary}. The theorem
identifies the $\SOneUp$ unit-equation use of RealAlgOrder apartness with the
same endpoint witnesses, real component rows, product carrier, unit-equation
witness, componentwise classifier rows, and equation transports.

Then feed the underlying apartness row through
\autoref{thm:realalgorder-metricspace-public-positive-distance-handoff}. This
records the positive-distance component consumed by $\MetricSpaceUp$ while
leaving the rational endpoints, $\RealUp$ names, $\hsame$ rows, $\Cont$ routes,
$\Pkg$ provenance, and local $\NameCert$ rows unchanged.

Apply
\autoref{thm:realalgorder-metricspace-sone-positive-boundary} to identify the
common package seen by both consumers. Since that package has only the displayed
constant-rational, metric-distance, product, unit-equation, transport,
provenance, and certificate rows, an angle quotient or completed-real equality
row has no source coordinate from which it can be read.
\end{proof}

\begin{theorem}[RealAlgOrder metric consumer order stability]
\label{thm:realalgorder-metric-consumer-order-stability}
For constant rational real names, every $\MetricSpaceUp$ positive-distance
consumer obtained from a $\RealAlgOrderUp$ apartness packet preserves the
original RealAlgOrder order and apartness row under the displayed $\RealUp$
classifier transport. The consumer may read the positive-distance component,
endpoint witnesses, $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and
local $\NameCert$ row, but the transported order and apartness source remains
the same $\RealAlgOrderUp$ row certified by the constant-rational interface.

The stability statement does not assert trichotomy, quotient equality, host
metric structure, compactness, connectedness, or Real completeness.
\end{theorem}
\begin{proof}
Start from
\autoref{thm:realalgorder-constant-transported-classifier-congruence}. It says
that the algebra, order, apartness, and public metric-facing rows are transported
from the same rational classifier surface through the displayed $\RealUp$
constant classifier.

Next apply
\autoref{thm:realalgorder-metricspace-public-positive-distance-handoff}. The
$\MetricSpaceUp$ consumer receives the positive-distance component by repacking
the RealAlgOrder apartness row, so the metric-facing read has the same endpoint
witnesses, $\hsame$ rows, continuation routes, provenance, and local certificate.

Finally use
\autoref{thm:realalgorder-apartness-metric-consumer-separation} together with
\autoref{thm:realalgorder-metricspace-sone-positive-boundary}. These results
limit the consumer surface to the displayed order, apartness, metric-distance,
transport, continuation, provenance, and certificate rows. The order/apartness
row is therefore stable under classifier transport, and no trichotomy, quotient
equality, host metric, compactness, connectedness, or completeness coordinate is
created by the metric consumer.
\end{proof}
