\begin{definition}[Real RegSeqRat StreamName dependency triple]
\label{def:real-regseq-streamname-dependency-triple}
A $\RealUp$ RegSeqRat StreamName dependency triple is a finite
$\mathsf{BHist}$ packet
$$
(S,Q,D,R,H,C,P,N)
$$
whose visible rows have the following shape:
\begin{enumerate}
\item $S$ records the inspected $\StreamNameUp$ finite windows and their
  transported stream-name classifier rows;
\item $Q$ records the $\RegSeqRatUp$ readback surface over the same scheduled
  windows;
\item $D$ records the $\DyadicRatCoreUp$ observation ledger read pointwise
  through those windows;
\item $R$ records the $\RealUp$ seal row and its finite endpoint readback;
\item $H$ records componentwise $\hsame$ comparisons for the window,
  readback, dyadic, and seal rows;
\item $C$ records the displayed $\Cont$ route from each public seal read to
  the preceding window, readback, dyadic, and seal coordinates;
\item $P$ records the $\Pkg$ provenance for the four sibling surfaces;
\item $N$ is the local $\NameCert$ row for this dependency packet.
\end{enumerate}
The classifier compares dependency triples only through these displayed rows.
It has no coordinate for a quotient real, selected host limit, host equality,
ambient completeness principle, arithmetic package, order package, or
metric-completeness row.
\end{definition}

\begin{theorem}[Real RegSeqRat StreamName seal-route exhaustion]
\label{thm:real-regseq-streamname-seal-route-exhaustion}
Every accepted $\RealUp$ seal read from a dependency triple
$(S,Q,D,R,H,C,P,N)$ factors through the $\StreamNameUp$ finite window row
$S$, then the $\RegSeqRatUp$ readback row $Q$, then the
$\DyadicRatCoreUp$ ledger row $D$, and only then the $\RealUp$ seal row $R$.
The factorization is transported by the componentwise $\hsame$ row $H$, read
through the displayed $\Cont$ route $C$, and packaged by $P,N$.

Consequently the accepted seal route is exactly the sibling route through
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-dyadicratcore-namecert} before the
$\RealUp$ seal is consumed. It exports no quotient real, selected host limit,
host equality, ambient completeness coordinate, arithmetic package, order
package, or metric-completeness row.
\end{theorem}
\begin{proof}
Begin with an accepted seal read from $(S,Q,D,R,H,C,P,N)$. The definition of
the dependency triple exposes only the finite window row $S$, regular
rational readback $Q$, dyadic observation ledger $D$, seal row $R$, and the
transport, route, package, and local naming rows $H,C,P,N$.

Use \autoref{thm:realup-regseqrat-streamname-seal-handoff}. That handoff
identifies the $\RealUp$ seal-facing package as the stream-name classifier
row, transported unary classifier row, finite-window ledger, endpoint
readback, and seal provenance.

Now read the upstream sibling surfaces. The StreamName, RegSeqRat, and
DyadicRatCore chapters named in
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-dyadicratcore-namecert} provide exactly the
window, readback, and dyadic ledger rows used by the handoff. The displayed
$H,C,P,N$ rows keep those coordinates in one $\mathsf{BHist}$ packet.

Since the packet has no remaining coordinate after $R$, a public seal read
cannot branch to a quotient real, selected host limit, host equality, ambient
completeness principle, arithmetic or order package, or metric-completeness
row. Thus every accepted read is exhausted by the stated route.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName Cauchy-completion interface]
\label{thm:real-regseq-streamname-cauchy-completion-interface}
For the current $\RealUp$ completion-facing phase, the Cauchy-completion
interface exposed by a Real RegSeqRat StreamName dependency triple is exactly
the finite route through
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert},
\autoref{ch:concrete-instances-dyadicratcore-namecert}, and the local
$\RealUp$ seal row. Any completion-facing consumer must factor through this
route before it reads a $\RealUp$ endpoint.

The interface exports the displayed finite window, regular-rational readback,
dyadic observation ledger, seal row, componentwise $\hsame$ transport,
displayed $\Cont$ route, package provenance, and local $\NameCert$ row. It
exports no quotient stream, selected host limit, representative choice,
host equality, ambient completeness principle, arithmetic package, order
package, or metric-completeness row.
\end{theorem}
\begin{proof}
Start from the dependency triple of
\autoref{def:real-regseq-streamname-dependency-triple}. Its only inbound
sibling rows are the finite $\StreamNameUp$ window $S$, the
$\RegSeqRatUp$ readback row $Q$, and the $\DyadicRatCoreUp$ ledger row $D$,
with the $\RealUp$ seal row $R$ placed after them in the same finite packet.

Apply the seal-route exhaustion theorem
\autoref{thm:real-regseq-streamname-seal-route-exhaustion}. It identifies
every accepted seal read as the route through $S$, then $Q$, then $D$, and
only then $R$, transported by $H$, read through $C$, and packaged by $P,N$.

The local seal row is therefore the completion-facing boundary. Since the
packet has no coordinate for quotient streams, selected host limits,
representative choice, host equality, completeness, arithmetic, order, or
metric completeness, a consumer cannot read any of those objects before or
after the $\RealUp$ endpoint. The only available interface is the stated
finite route.
\end{proof}

\begin{theorem}[Real open-phase dependency triple current surface]
\label{thm:real-open-phase-dependency-triple-current-surface}
Every current Phase Real and completion-facing $\RealUp$ seal consumer of the
dependency triple
$$
(S,Q,D,R,H,C,P,N)
$$
factors through exactly four displayed faces: the $\DyadicRatCoreUp$
observation face $D$, the $\StreamNameUp$ finite-window face $S$, the
$\RegSeqRatUp$ regularity and readback face $Q$, and the local $\RealUp$ seal
face $R$. The factorization is transported only by the displayed
componentwise $\hsame$ row $H$, the $\Cont$ route row $C$, the $\Pkg$
provenance row $P$, and the local $\NameCert$ row $N$.

Conversely, those four faces together with $H,C,P,N$ assemble the accepted
current surface for such consumers. The surface has no coordinate for quotient
streams, host equality, selected limits, ambient completeness, arithmetic
packages, order packages, or metric-completeness rows.
\end{theorem}
\begin{proof}
Start with the displayed dependency triple of
\autoref{def:real-regseq-streamname-dependency-triple}. Its carrier rows are
exactly $S,Q,D,R,H,C,P,N$, so any current consumer must begin from those
coordinates.

Apply \autoref{thm:real-regseq-streamname-seal-route-exhaustion}. It exhausts
each accepted seal route by the finite-window row $S$, the regular readback row
$Q$, the dyadic observation row $D$, and the local seal row $R$, transported
through $H,C,P,N$.

Apply \autoref{thm:real-regseq-streamname-cauchy-completion-interface}. The
same route is the completion-facing interface before a $\RealUp$ endpoint is
read, so Phase Real and completion RealUp seal consumers share the displayed
four-face surface.

For the converse, assemble the accepted surface from the four listed faces and
the transport, route, provenance, and certificate rows. The exclusion clause in
the dependency triple removes quotient streams, host equality, selected
limits, ambient completeness, arithmetic packages, order packages, and
metric-completeness rows, leaving no further coordinate to add.
\end{proof}

\begin{theorem}[Real seal RegSeqRat StreamName dependency exhaustion]
\label{thm:real-seal-regseq-streamname-dependency-exhaustion}
Every accepted $\RealUp$ seal consumer that reads the dependency triple of
\autoref{def:real-regseq-streamname-dependency-triple} factors through
exactly the finite rows supplied by $\DyadicRatCoreUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local
$\NameCert$ row.

The same consumer exports no quotient stream, selected host limit,
representative choice, host equality, ambient completeness principle,
arithmetic package, order package, or metric-completeness row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-regseq-streamname-seal-route-exhaustion} to the seal
read. It identifies the only accepted route as the path through the finite
$\StreamNameUp$ window row, the $\RegSeqRatUp$ readback row, the
$\DyadicRatCoreUp$ ledger row, and the local $\RealUp$ seal row, transported
by $\hsame$, read through $\Cont$, and packaged by $\Pkg$ and $\NameCert$.

Apply \autoref{thm:real-regseq-streamname-cauchy-completion-interface}. It
turns the same finite route into the completion-facing interface and states
that every completion-facing consumer must read through that interface before
it reaches a $\RealUp$ endpoint.

Finally project the dependency triple itself. Its displayed coordinates are
only $(S,Q,D,R,H,C,P,N)$, and its exclusion clause contains no quotient
stream, selected host limit, representative choice, host equality, ambient
completeness principle, arithmetic package, order package, or
metric-completeness row. Hence there is no non-finite route for the consumer
to export.
\end{proof}

\begin{theorem}[Real finite-window completion boundary]
\label{thm:real-finite-window-completion-boundary}
For any accepted $\RealUp$ RegSeqRat StreamName dependency triple
$(S,Q,D,R,H,C,P,N)$, every completion-facing $\RealUp$ consumer factors through
the finite $\StreamNameUp$ window row $S$, the $\RegSeqRatUp$ readback row $Q$,
the $\DyadicRatCoreUp$ ledger row $D$, and the local $\RealUp$ seal row $R$.
The passage is transported by the componentwise $\hsame$ row $H$, read through
the displayed $\Cont$ route $C$, and packaged by $\Pkg$ provenance and the
local $\NameCert$ row $N$.

No quotient stream, selected host limit, representative choice, host equality,
ambient completeness principle, arithmetic package, order package, or
metric-completeness row is exported by this completion-facing boundary.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-regseq-streamname-seal-route-exhaustion}. It gives the
only seal-facing route through the finite $\StreamNameUp$, $\RegSeqRatUp$,
$\DyadicRatCoreUp$, and local $\RealUp$ seal rows, with the displayed
$H,C,P,N$ transport, continuity, package, and naming data.

Next apply
\autoref{thm:real-regseq-streamname-cauchy-completion-interface}. This turns
the same finite route into the completion-facing interface and forces every
completion consumer to pass through it before reading a $\RealUp$ endpoint.

Finally use the coordinate exclusion clause in
\autoref{def:real-regseq-streamname-dependency-triple}. The accepted packet
has only the rows $(S,Q,D,R,H,C,P,N)$, so no quotient stream, selected host
limit, representative choice, host equality, ambient completeness principle,
arithmetic package, order package, or metric-completeness row can be exported.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName seal-source minimality]
\label{thm:real-regseq-streamname-seal-source-minimality}
For an accepted $\RealUp$ RegSeqRat StreamName dependency triple
$(S,Q,D,R,H,C,P,N)$, the current accepted seal source is minimal in its four
open-phase faces. Removing any one of the $\DyadicRatCoreUp$ observation face
$D$, the $\StreamNameUp$ finite-window face $S$, the $\RegSeqRatUp$ readback
face $Q$, or the local $\RealUp$ seal face $R$ leaves no accepted current
Phase Real or Completion seal source.

The transport, continuation, package, and local certificate rows $H,C,P,N$
do not replace a missing face. They only carry and name the route after all
four faces are present in the displayed dependency triple.
\end{theorem}
\begin{proof}
Start from the route exhaustion of
\autoref{thm:real-regseq-streamname-seal-route-exhaustion}. It places every
accepted seal read on the finite path through $S$, then $Q$, then $D$, and
only then $R$, with $H,C,P,N$ carrying that displayed path.

Use the current-surface theorem
\autoref{thm:real-open-phase-dependency-triple-current-surface}. Its
converse assembles the accepted current surface from precisely the four
faces together with $H,C,P,N$, and its exclusion clause leaves no quotient,
host, completeness, arithmetic, order, or metric-completeness coordinate
outside them.

Now delete one face. If $S$ is absent, there is no finite-window source for
the readback. If $Q$ is absent, there is no regular-rational readback for the
dyadic observation ledger. If $D$ is absent, there is no dyadic observation
face for the seal route. If $R$ is absent, there is no local Real seal for
the endpoint read. In each case the Cauchy-completion interface of
\autoref{thm:real-regseq-streamname-cauchy-completion-interface} has no
accepted endpoint route, so no current seal source remains.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName current-phase gate]
\label{thm:real-regseq-streamname-current-phase-gate}
Every current Phase Real and Completion consumer of an accepted dependency
triple $(S,Q,D,R,H,C,P,N)$ must enter through the four-face route
$$
S,\quad Q,\quad D,\quad R
$$
before it reads a $\RealUp$ endpoint. The gate is carried only by the
componentwise $\hsame$ row $H$, the displayed $\Cont$ route $C$, the $\Pkg$
provenance $P$, and the local $\NameCert$ row $N$.

No endpoint read is licensed from quotient streams, selected host limits,
representative choices, host equality, ambient completeness, arithmetic or
order packages, or metric-completeness rows.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-regseq-streamname-cauchy-completion-interface}. It states
that every completion-facing consumer must pass through the finite
StreamName, RegSeqRat, DyadicRatCore, and local Real seal route before
reading a $\RealUp$ endpoint.

Next apply
\autoref{thm:real-finite-window-completion-boundary}. The boundary repeats
the same entry order for completion-facing consumers and identifies $H,C,P,N$
as the only transport, route, provenance, and certificate rows attached to
that entry.

Finally apply
\autoref{thm:real-regseq-streamname-seal-source-minimality}. Since no one of
the four faces can be removed while retaining an accepted current seal
source, the entry route is a gate rather than an optional presentation of the
endpoint.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName no completion escape]
\label{thm:real-regseq-streamname-no-completion-escape}
Completion-facing consumers of an accepted $\RealUp$ RegSeqRat StreamName
dependency triple cannot bypass the four faces through quotient streams,
selected host limits, representative choices, host equality, ambient
completeness, arithmetic packages, order packages, or metric-completeness
rows. Their only accepted completion route is the displayed path through the
$\StreamNameUp$ finite-window face, the $\RegSeqRatUp$ readback face, the
$\DyadicRatCoreUp$ observation face, and the local $\RealUp$ seal face.
\end{theorem}
\begin{proof}
Use route exhaustion to identify the only seal-facing path. By
\autoref{thm:real-regseq-streamname-seal-route-exhaustion}, that path is the
displayed finite route through $S,Q,D,R$ with $H,C,P,N$.

Use the current-phase gate to place every Phase Real and Completion endpoint
read behind the same path. A completion-facing consumer therefore cannot
reach the endpoint before the four faces have all been read.

It remains to exclude escape coordinates. The finite-window completion
boundary of \autoref{thm:real-finite-window-completion-boundary} and the
Cauchy-completion interface of
\autoref{thm:real-regseq-streamname-cauchy-completion-interface} both remove
quotient streams, selected host limits, representative choices, host
equality, ambient completeness, arithmetic and order packages, and
metric-completeness rows from the exported boundary. Since minimality also
prevents deleting any face, there is no completion route outside the four
displayed faces.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName endpoint determinacy]
\label{thm:real-regseq-streamname-endpoint-determinacy}
Let $(S,Q,D,R,H,C,P,N)$ and $(S',Q',D',R',H',C',P',N')$ be accepted
$\RealUp$ RegSeqRat StreamName dependency triples. Suppose the displayed
$\StreamNameUp$ finite-window rows $S,S'$ are compared only by the advertised
$\hsame$ transport rows in $H,H'$, and suppose the $\RegSeqRatUp$ readback
rows $Q,Q'$ together with the $\DyadicRatCoreUp$ ledger rows $D,D'$ are the
same displayed route through
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert}, and
\autoref{ch:concrete-instances-dyadicratcore-namecert}.

Then any public $\RealUp$ endpoint comparison between the two consumers
factors only through the finite packets
$$
(S,Q,D,R,H,C,P,N)
\quad\text{and}\quad
(S',Q',D',R',H',C',P',N').
$$
In particular the comparison has no coordinate for quotient streams, host
real equality, selected host limits, representative choice, ambient
completeness, arithmetic or order packages, or metric-completeness rows.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-regseq-streamname-seal-route-exhaustion} to each accepted
consumer. Each endpoint read reaches the $\RealUp$ seal only through its
displayed $\StreamNameUp$ finite-window row, $\RegSeqRatUp$ readback row,
$\DyadicRatCoreUp$ ledger row, local seal row, $\hsame$ transport,
$\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row.

Next use
\autoref{thm:real-regseq-streamname-cauchy-completion-interface}. The
completion-facing boundary is therefore the same finite route, so an endpoint
comparison cannot consult data outside the two displayed packets before it
compares the public endpoints.

Finally apply
\autoref{thm:real-seal-regseq-streamname-dependency-exhaustion}. That theorem
exhausts the coordinate supply for every accepted seal consumer by the rows
named in the dependency triple. Since the hypotheses identify the window,
readback, and dyadic route through the three sibling chapters, the remaining
public comparison is determined by the two finite packets alone, with no
quotient-stream, host-equality, selected-limit, representative-choice,
ambient-completeness, arithmetic, order, or metric-completeness coordinate
available.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName finite-window pullback classifier]
\label{thm:real-regseq-streamname-finite-window-pullback-classifier}
Let
$$
X=(S,Q,D,R,H,C,P,N)
\quad\text{and}\quad
Y=(S',Q',D',R',H',C',P',N')
$$
be accepted $\RealUp$ RegSeqRat StreamName dependency triples. The two triples
classify as the same completion-facing $\RealUp$ finite-window packet if and
only if all of the following displayed rows agree componentwise:
\begin{enumerate}
\item the $\StreamNameUp$ finite-window rows $S,S'$;
\item the $\RegSeqRatUp$ readback rows $Q,Q'$;
\item the $\DyadicRatCoreUp$ ledger rows $D,D'$;
\item the $\RealUp$ seal rows $R,R'$;
\item the componentwise $\hsame$ transports displayed in $H,H'$;
\item the displayed $\Cont$ routes in $C,C'$;
\item the $\Pkg$ provenance rows $P,P'$;
\item the local $\NameCert$ rows $N,N'$.
\end{enumerate}
Equivalently, the classifier for accepted Real RegSeqRat StreamName dependency
triples is the finite pullback of the four open-phase faces
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ together
with the displayed transport, route, provenance, and local naming rows. It has
no coordinate for quotient streams, host equality, selected limits, ambient
completeness, arithmetic or order packages, or metric-completeness rows.
\end{theorem}
\begin{proof}
For the forward direction, assume the two accepted triples classify as the
same completion-facing finite-window packet. Apply
\autoref{thm:real-regseq-streamname-seal-route-exhaustion} to both triples.
Each accepted route is exhausted by the displayed $\StreamNameUp$,
$\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows.

Now apply \autoref{thm:real-regseq-streamname-endpoint-determinacy}. Since a
public endpoint comparison cannot consult any coordinate outside those finite
packets, equality of the completion-facing packet projects to componentwise
agreement of the stream-name window, regular readback, dyadic ledger, real
seal, transport, route, provenance, and local naming rows.

For the reverse direction, assume the eight displayed rows agree
componentwise. Use
\autoref{thm:realup-open-phase-four-face-pullback} to repack the four
open-phase faces as a single finite pullback packet. The matching $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows provide exactly the gluing data required
by that pullback.

Finally read the resulting packet through
\autoref{def:real-regseq-streamname-dependency-triple}. The local dependency
triple definition accepts precisely those rows as the completion-facing Real
finite-window packet, so the two accepted triples classify the same packet.
The exclusion clause in the definition removes quotient streams, host
equality, selected limits, ambient completeness, arithmetic and order packages,
and metric-completeness rows from the classifier.
\end{proof}

\begin{theorem}[Real RegSeqRat StreamName dyadic window lock]
\label{thm:real-regseq-streamname-dyadic-window-lock}
Let
$$
X=(S,Q,D,R,H,C,P,N)
\quad\text{and}\quad
Y=(S',Q',D',R',H',C',P',N')
$$
be accepted $\RealUp$ RegSeqRat StreamName dependency triples. Suppose the
displayed $\StreamNameUp$ finite-window rows $S,S'$, the $\RegSeqRatUp$
readback rows $Q,Q'$, the $\DyadicRatCoreUp$ ledger rows $D,D'$, and the
$\RealUp$ seal rows $R,R'$ agree componentwise under the shown $\hsame$
transports in $H,H'$, the displayed $\Cont$ routes in $C,C'$, the package rows
$P,P'$, and the local $\NameCert$ rows $N,N'$.

Then every completion-facing $\RealUp$ consumer comparison between $X$ and $Y$
factors through exactly the common finite four-face window lock
$$
(S,Q,D,R,H,C,P,N)\simeq(S',Q',D',R',H',C',P',N').
$$
That lock is the shared pullback of the $\StreamNameUp$ finite-window face, the
$\RegSeqRatUp$ readback face, the $\DyadicRatCoreUp$ ledger face, and the local
$\RealUp$ seal face, with no quotient stream, selected host limit, host
equality, representative choice, ambient completeness principle,
arithmetic package, order package, or metric-completeness row.
\end{theorem}
\begin{proof}
First apply \autoref{thm:real-regseq-streamname-seal-route-exhaustion} to both
accepted triples. Each seal-facing route is exhausted by the displayed
$\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\hsame$,
$\Cont$, $\Pkg$, and local $\NameCert$ rows.

Next apply \autoref{thm:real-regseq-streamname-cauchy-completion-interface}.
It turns the same exhausted route into the completion-facing boundary, so a
consumer comparison has no access to data before or after the finite route
except through the rows shown in the two packets.

Use \autoref{thm:real-seal-regseq-streamname-dependency-exhaustion} to remove
the remaining escape coordinates. Quotient streams, selected limits,
representative choices, host equality, ambient completeness, arithmetic and
order packages, and metric-completeness rows are not coordinates of the
accepted dependency triples.

Finally apply
\autoref{thm:real-regseq-streamname-finite-window-pullback-classifier}. The
componentwise agreement hypotheses are exactly the pullback agreement
conditions for the four open-phase faces and their structural rows. Therefore
every completion-facing comparison factors through that common finite window
lock and through nothing larger.
\end{proof}

\begin{theorem}[Real L10 four-face route lock]
\label{thm:real-l10-four-face-route-lock}
Let
$$
X=(S,Q,D,R,H,C,P,N)
\quad\text{and}\quad
Y=(S',Q',D',R',H',C',P',N')
$$
be accepted $\RealUp$ RegSeqRat StreamName dependency triples. Every current
Phase Real and Completion consumer comparison between $X$ and $Y$ factors
through exactly the four open-phase faces
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad
\RegSeqRatUp,\qquad \RealUp .
$$
The only comparison structure available to that factorization is the
displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows in the two packets.

Thus no quotient stream, host equality, selected limit, ambient completeness,
arithmetic package, order package, or metric-completeness row is available to
the comparison. The comparison is locked to the local finite route through the
dyadic observation ledger, stream-name finite window, regular-rational
readback, and local real seal.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-regseq-streamname-seal-route-exhaustion}. It exhausts every
accepted seal-facing route by the displayed $\StreamNameUp$ finite-window row,
$\RegSeqRatUp$ readback row, $\DyadicRatCoreUp$ ledger row, local $\RealUp$
seal row, and the shown $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next apply
\autoref{thm:real-regseq-streamname-finite-window-pullback-classifier}. The
classifier for accepted Real RegSeqRat StreamName dependency triples is the
finite pullback of those four open-phase faces together with the displayed
structural rows, so a consumer comparison has no independent coordinate
outside that pullback.

Finally apply
\autoref{thm:real-regseq-streamname-dyadic-window-lock}. The common finite
window lock forces every completion-facing comparison between accepted packets
through the shared four-face window. Since the three results already remove
quotient streams, host equality, selected limits, ambient completeness,
arithmetic and order packages, and metric-completeness rows, the Real L10
comparison route is exactly the four-face route stated above.
\end{proof}
