\begin{theorem}[Real unary StreamNameUp finite-window selected denominator package]
\label{thm:real-unary-streamname-finite-window-selected-denominator-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,z_s,z_t:\Hist$, assume
$$
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega).
$$
Then the selected endpoints carry the finite-window denominator package:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(
s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-unary-streamname-finite-window-coverage} to the two
carrier fields projected from $\mathsf{RatStreamNameClassifier}(s,t)$, the
StreamNameUp classifier, and the unary anchor and bound. This gives
$\mathsf{RealUnaryStreamWindowClassifier}(s,t,\alpha,\omega)$.

Project this window classifier at the selected offset $k$ by
\autoref{lem:real-unary-stream-window-endpoint-projection}. The offset witness
$\mathsf{UnaryOffsetLe}(k,\omega)$ gives
$$
\mathsf{RatHistoryClassifier}(
s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k))).
$$

Apply \autoref{thm:rat-history-classifier-positive-denominators} to this
selected endpoint classifier. This supplies positive unary denominator witnesses
for both selected endpoints.

Apply \autoref{thm:positive-unary-denominator-unary-and-nonempty} separately to
the two positive-denominator rows. These projections give the two unary-history
rows and the two nonempty endpoint exclusions.

It remains to rule out selected zero heads. For the left endpoint, transport the
positive denominator witness along
$\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))$ by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}; the transported
witness contradicts \autoref{thm:rat-positive-denominator-e0-absurd}.

The right endpoint is identical, using the displayed comparison with
$\Ezero(z_t)$. The same transport and zero-head absurdity theorem give the
second zero-head exclusion, and all rows together form the displayed package.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_denominator\_package}

\begin{theorem}[Real unary StreamNameUp finite-window selected shape package]
\label{thm:real-unary-streamname-finite-window-selected-shape-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,u,v,z_s,z_t:\Hist$, assume
$$
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega),
$$
and the displayed selected window endpoints
$$
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u)),
\quad
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v)).
$$
Then the selected endpoints carry the finite-window RatUp readback package:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land
\mathsf{UnaryHistory}(u)\land
\mathsf{UnaryHistory}(v)\land
\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-denominator-package}
to the StreamNameUp classifier, the unary anchor and bound, the selected
offset, and the two zero-head tests. Inside that package, the carrier rows are
the two fields projected from $\mathsf{RatStreamNameClassifier}(s,t)$. This
supplies the selected RatUp classifier, the positive-denominator rows, the
unary endpoint rows, the nonempty exclusions, and the two zero-head exclusions.

The selected RatUp classifier is the first row of the selected shape package.
Transport the selected RatUp classifier across the two displayed $\Eone$
endpoint comparisons by \autoref{thm:rat-history-classifier-hsame-transport}.
The transported classifier is
$\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))$.

Apply \autoref{thm:rat-history-classifier-e1-tail-unary-iff} in the forward
direction to the transported $\Eone$ classifier. This reads back
$\mathsf{UnaryHistory}(u)$, $\mathsf{UnaryHistory}(v)$, and $\hsame(u,v)$.
Together with the denominator package rows, these are exactly the displayed
finite-window selected shape package.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_shape\_package}

Fit. Traditional target: selected finite-window rational readback for RealUp
StreamNameUp classifiers. BEDC source: $\StreamNameUp+\RealUp+\RatUp$ over
$\mathsf{BHist}$. Carrier: $\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: $\hsame$ transport of
selected endpoints and positive-denominator transport. Ledger: anchor, bound,
offset, selected endpoint displays, and zero-head tests. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-shape-package}.
Exactness: selected source RatUp classifier, displayed RatUp one-tail classifier,
denominator, unary, nonempty, and zero-headed exclusion rows. Standard bridge:
finite rational observation windows. Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected common e-one tail readback]
\label{thm:real-unary-streamname-finite-window-selected-common-e1-tail-readback}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k:\Hist$, assume
$$
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega).
$$
Then the selected endpoints admit common one-headed unary readback:
$$
\exists u,v:\Hist,\
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v))\land
\mathsf{UnaryHistory}(u)\land
\mathsf{UnaryHistory}(v)\land
\hsame(u,v).
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-denominator-package}
to the StreamNameUp classifier, the unary anchor and bound, the selected
offset, and arbitrary zero-head tests. This supplies the selected RatUp
classifier, the positive-denominator rows, the unary endpoint rows, and the
nonempty endpoint exclusions.

Use \autoref{thm:unary-history-nonempty-e1-tail} separately on the two selected
endpoints. The left endpoint yields a tail $u$ with
$\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u))$ and
$\mathsf{UnaryHistory}(u)$. The right endpoint yields a tail $v$ with
$\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v))$ and
$\mathsf{UnaryHistory}(v)$.

Transport the selected RatUp classifier across these two displayed endpoint
rows by \autoref{thm:rat-history-classifier-hsame-transport}. The transported
classifier is $\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))$.

Apply \autoref{thm:rat-history-classifier-e1-tail-unary-iff} in the forward
direction to the transported classifier. This reads back the common tail row
$\hsame(u,v)$. Package $u$ and $v$ with the two displayed endpoint rows, the
two unary-tail rows, and the common-tail row.
\end{proof}

Fit. Traditional target: selected finite-window RealUp endpoint witness
readback without displayed endpoint assumptions. BEDC source:
$\StreamNameUp+\RealUp+\RatUp$ over $\mathsf{BHist}$. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through selected
$\mathsf{RatHistoryClassifier}$. Stability: $\hsame$ endpoint transport from
selected endpoints to e-one displays. Ledger: anchor, bound, selected offset,
positive denominator rows, unary endpoint rows, and nonempty exclusions. Core
theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-common-e1-tail-readback}.
Exactness: existential one-headed endpoints with unary tails and common tail
comparison. Standard bridge: finite rational observation windows. Status:
$\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected full endpoint package]
\label{thm:real-unary-streamname-finite-window-selected-full-endpoint-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,u,v,z_s,z_t:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega),
$$
and the displayed selected window endpoints
$$
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u)),
\quad
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v)).
$$
Then the selected endpoints carry the full finite-window endpoint package:
$$
\begin{array}{l}
\mathsf{RealUnaryStreamWindowClassifier}(s,t,\alpha,\omega)\land\\
\mathsf{RatHistoryClassifier}(s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land\mathsf{UnaryHistory}(v)\land\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-unary-streamname-finite-window-coverage} to the two
carrier rows, the StreamNameUp classifier, and the unary anchor and bound. This
produces $\mathsf{RealUnaryStreamWindowClassifier}(s,t,\alpha,\omega)$.

Apply \autoref{lem:real-unary-stream-window-endpoint-projection} to that window
classifier and the displayed offset witness $\mathsf{UnaryOffsetLe}(k,\omega)$.
This gives the selected source classifier
$$
\mathsf{RatHistoryClassifier}(
s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k))).
$$

Apply
\autoref{thm:real-unary-streamname-finite-window-selected-shape-package} to the
same hypotheses. It supplies the transported $\Eone$ classifier, the unary tail
readback, the two positive-denominator rows, the two unary endpoint rows, the
nonempty exclusions, and the zero-head exclusions.

Combining the window classifier, the projected selected classifier, and the
selected shape package gives exactly the displayed full endpoint package.
\end{proof}

Fit. Traditional target: RealUp finite-window selected full endpoint readback.
BEDC source: $\StreamNameUp+\RealUp+\RatUp$. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: $\hsame$ endpoint
transport with positive-denominator transport. Ledger: carrier, classifier,
unary anchor, unary bound, selected offset, endpoint displays, and zero-head
tests. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-full-endpoint-package}.
Exactness: selected classifier plus the displayed endpoint package. Standard
bridge: downstream finite rational observation windows. Status:
$\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected classifier appended-tail package]
\label{thm:real-unary-streamname-finite-window-selected-classifier-appended-tail-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,u,v,z_s,z_t,d_s,d_t:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega),
$$
and the displayed selected window endpoints
$$
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u)),
\quad
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v)).
$$
Then the selected endpoints carry the selected-shape endpoint package and the
appended e-zero-tail exclusions:
$$
\begin{array}{l}
\mathsf{RatHistoryClassifier}(s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land\mathsf{UnaryHistory}(v)\land\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))\to
\mathsf{False})\land\\
(\hsame(t(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))\to
\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-shape-package}
to the two carrier rows, the StreamNameUp classifier, the unary anchor and
bound, the selected offset, and the displayed one-headed endpoint comparisons.
This gives every selected endpoint row through the zero-head exclusions,
including the two selected positive-denominator witnesses.

For the left endpoint, suppose
$\hsame(s(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))$. Transport the
positive denominator witness for $s(\mathsf{append}(\alpha,k))$ across this
displayed sameness by
\autoref{thm:rat-positive-unary-denominator-hsame-transport}. The transported
witness is a positive unary denominator witness for $d_s\cdot\Ezero(z_s)$,
contradicting
\autoref{thm:positive-unary-denominator-append-e0-tail-absurd}.

The right endpoint is identical. A display
$\hsame(t(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))$ transports the
positive denominator witness for $t(\mathsf{append}(\alpha,k))$ to
$d_t\cdot\Ezero(z_t)$, and the same appended e-zero-tail absurdity theorem
contradicts that transported witness.

Repack the original selected-shape rows with the two appended-tail exclusions.
This is exactly the displayed selected classifier appended-tail package.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_classifier\_appended\_tail\_package}

Fit. Traditional target: selected finite-window rational readback with
appended-tail endpoint exclusion for RealUp StreamNameUp classifiers. BEDC
source: $\StreamNameUp+\RealUp+\RatUp$ over $\mathsf{BHist}$. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: $\hsame$ transport of
selected endpoints and positive-denominator transport to appended tails.
Ledger: carrier, classifier, unary anchor, unary bound, selected offset,
one-headed endpoint displays, zero-head tests, and appended-tail displays. Core
theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-classifier-appended-tail-package}.
Exactness: the full selected endpoint package plus the two appended e-zero-tail
exclusion rows. Standard bridge: finite rational observation windows. Status:
$\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected e-one tail coverage package]
\label{thm:real-unary-streamname-finite-window-selected-e1-tail-coverage-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,z_s,z_t,d_s,d_t:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega).
$$
Then there exist histories $u,v:\Hist$ such that the selected endpoints are
displayed as e-one endpoints and, for those witnesses, the full endpoint rows
and appended e-zero-tail exclusions hold:
$$
\begin{array}{l}
\exists u,v,\,
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v))\land\\
\mathsf{RealUnaryStreamWindowClassifier}(s,t,\alpha,\omega)\land\\
\mathsf{RatHistoryClassifier}(s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land\mathsf{UnaryHistory}(v)\land\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))\to
\mathsf{False})\land\\
(\hsame(t(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))\to
\mathsf{False}).
\end{array}
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-denominator-package}
to the StreamNameUp classifier, the unary anchor and bound, the selected
offset, and the two zero-head tests. The package supplies the selected RatUp
classifier, the two positive unary denominator rows, the two unary selected
endpoint rows, the two nonempty endpoint exclusions, and the two zero-head
exclusions.

Apply \autoref{thm:unary-history-nonempty-e1-tail} to the left unary endpoint
row and its nonempty exclusion. This chooses a tail $u$, and the constructor
equality supplies the $\hsame$ display from $s(\mathsf{append}(\alpha,k))$ to
$\Eone(u)$. The same theorem applied to the right unary endpoint row and
nonempty exclusion chooses a tail $v$ and supplies the $\hsame$ display from
$t(\mathsf{append}(\alpha,k))$ to $\Eone(v)$.

Feed the two e-one endpoint displays, together with the carrier rows, classifier
row, unary anchor and bound, selected offset, zero-head tests, and appended-tail
tests, into
\autoref{thm:real-unary-streamname-finite-window-selected-classifier-appended-tail-package}.
That theorem returns the full selected endpoint package and the two appended
e-zero-tail exclusions for the chosen witnesses $u$ and $v$.

Package $u$ and $v$ as the existential witnesses. Prepending their two selected
endpoint displays to the returned appended-tail package gives exactly the
displayed coverage package.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_e1\_tail\_coverage\_package}

Fit. Traditional target: finite RealUp observation-window readback without
endpoint display hypotheses. BEDC source: $\StreamNameUp$ plus $\RealUp$ finite
windows plus $\RatUp$ denominator readback. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: $\hsame$ transport plus
unary nonempty e-one-tail decomposition. Ledger: anchor, bound, offset,
zero-head tests, and appended-tail tests. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-e1-tail-coverage-package}.
Exactness: existential e-one tails plus the full selected endpoint package.
Standard bridge: finite rational observation windows. Status:
$\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected e-one tail pairwise coherence]
\label{thm:real-unary-streamname-finite-window-selected-e1-tail-pairwise-coherence}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,a,a',b,b':\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega),
$$
and the four displayed selected e-one endpoint comparisons
$$
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(a)),\quad
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(a')),
$$
$$
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(b)),\quad
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(b')).
$$
Then the displayed tails form one pairwise selected-tail class:
\begin{enumerate}
\item $\mathsf{UnaryHistory}(a)$.
\item $\mathsf{UnaryHistory}(a')$.
\item $\mathsf{UnaryHistory}(b)$.
\item $\mathsf{UnaryHistory}(b')$.
\item $\hsame(a,a')$.
\item $\hsame(b,b')$.
\item $\hsame(a,b)$.
\item $\hsame(a',b')$.
\item $\hsame(a,b')$.
\item $\hsame(a',b)$.
\end{enumerate}
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-shape-package} to the
first left and right endpoint displays, together with the StreamNameUp classifier,
the unary anchor and bound, and the selected offset. This gives
$\mathsf{UnaryHistory}(a)$, $\mathsf{UnaryHistory}(b)$, and $\hsame(a,b)$.

Apply the same selected shape package to the primed left and right endpoint
displays. This gives $\mathsf{UnaryHistory}(a')$, $\mathsf{UnaryHistory}(b')$,
and $\hsame(a',b')$.

For the left selected endpoint, compose the symmetry of
$\hsame(s(\mathsf{append}(\alpha,k)),\Eone(a))$ with
$\hsame(s(\mathsf{append}(\alpha,k)),\Eone(a'))$. The kernel transitivity theorem
$\mathsf{BEDC.FKernel.Hist.hsame\_trans}$ gives
$\hsame(\Eone(a),\Eone(a'))$, and
$\mathsf{BEDC.FKernel.Hist.hsame\_e1\_iff}$ inverts the common e-one head to give
$\hsame(a,a')$.

The right selected endpoint is identical. Compose the symmetry of the displayed
comparison with $\Eone(b)$ and the displayed comparison with $\Eone(b')$, then
invert the common e-one head by
$\mathsf{BEDC.FKernel.Hist.hsame\_e1\_iff}$ to get $\hsame(b,b')$.

It remains to fill the two off-diagonal rows. Transitivity sends
$\hsame(a,a')$ and $\hsame(a',b')$ to $\hsame(a,b')$, while symmetry of
$\hsame(a,a')$ followed by $\hsame(a,b)$ gives $\hsame(a',b)$. Together with the
four unary rows and the two direct cross rows, these are exactly the ten displayed
claims.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_e1\_tail\_pairwise\_coherence}

\begin{theorem}[Real unary StreamNameUp finite-window selected canonical e-one tail witness]
\label{thm:real-unary-streamname-finite-window-selected-canonical-e1-tail-witness}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega).
$$
Then there exist histories $u,v:\Hist$ such that the selected endpoints have
canonical e-one tail displays and every other selected e-one display is coherent
with them:
$$
\begin{array}{l}
\exists u,v:\Hist,
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land
\mathsf{UnaryHistory}(v)\land
\hsame(u,v)\land\\
\forall u',v':\Hist,\,
\bigl(\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u'))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v'))\bigr)\to\\
\qquad
\mathsf{UnaryHistory}(u')\land
\mathsf{UnaryHistory}(v')\land
\hsame(u,u')\land
\hsame(v,v')\land\\
\qquad
\hsame(u',v)\land
\hsame(u,v').
\end{array}
$$
\end{theorem}
\begin{proof}
Instantiate
\autoref{thm:real-unary-streamname-finite-window-selected-e1-tail-coverage-package}
with the harmless choices $z_s=z_t=d_s=d_t=\emp$. The returned witnesses
$u$ and $v$ carry the two selected endpoint displays,
$\mathsf{UnaryHistory}(u)$, $\mathsf{UnaryHistory}(v)$, and $\hsame(u,v)$.

Now fix arbitrary histories $u',v'$ with the same selected endpoint displays.
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-e1-tail-pairwise-coherence}
with $a=u$, $a'=u'$, $b=v$, and $b'=v'$. The hypotheses are the carrier,
classifier, unary anchor, unary bound, selected offset, the chosen endpoint
displays, and the arbitrary endpoint displays.

Project the ten rows returned by pairwise coherence. They give
$\mathsf{UnaryHistory}(u')$, $\mathsf{UnaryHistory}(v')$, $\hsame(u,u')$,
$\hsame(v,v')$, $\hsame(u',v)$, and $\hsame(u,v')$. Repack these rows under the
universal clause and then package the chosen $u$ and $v$ as the displayed
canonical selected-tail witnesses.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealUnaryStreamWindowClassifier\_selected\_canonical\_e1\_tail\_witness}

Fit. Traditional target: canonical finite rational observation tail. BEDC
source: $\StreamNameUp$ plus $\RealUp$ plus $\RatUp$ plus $\mathsf{FKernel}$
e-one inversion. Carrier: $\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: endpoint $\hsame$ and
pairwise tail coherence. Ledger: anchor, bound, offset, and selected endpoint
displays. Core
theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-canonical-e1-tail-witness}.
Exactness: existence plus uniqueness up to $\hsame$. Standard bridge: finite
rational observation windows for RegSeqRat. Status: $\mathsf{ProofTarget}$.

\begin{theorem}[Real unary StreamNameUp finite-window selected canonical e-one tail full package]
\label{thm:real-unary-streamname-finite-window-selected-canonical-e1-tail-full-package}
For observation maps $s,t:\Hist\to\Hist$ and histories
$\alpha,\omega,k,z_s,z_t,d_s,d_t:\Hist$, assume
$$
\mathsf{RatStreamNameCarrier}(s),\quad
\mathsf{RatStreamNameCarrier}(t),\quad
\mathsf{RatStreamNameClassifier}(s,t),
$$
$$
\mathsf{UnaryHistory}(\alpha),\quad
\mathsf{UnaryHistory}(\omega),\quad
\mathsf{UnaryOffsetLe}(k,\omega).
$$
Then there exist histories $u,v:\Hist$ such that the selected endpoints carry
the complete displayed e-one certificate and every other selected e-one display
is coherent with those witnesses:
$$
\begin{array}{l}
\exists u,v:\Hist,
\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v))\land\\
\mathsf{RealUnaryStreamWindowClassifier}(s,t,\alpha,\omega)\land\\
\mathsf{RatHistoryClassifier}(s(\mathsf{append}(\alpha,k)),t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{RatHistoryClassifier}(\Eone(u),\Eone(v))\land\\
\mathsf{UnaryHistory}(u)\land\mathsf{UnaryHistory}(v)\land\hsame(u,v)\land\\
\mathsf{PositiveUnaryDenominator}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{PositiveUnaryDenominator}(t(\mathsf{append}(\alpha,k)))\land\\
\mathsf{UnaryHistory}(s(\mathsf{append}(\alpha,k)))\land
\mathsf{UnaryHistory}(t(\mathsf{append}(\alpha,k)))\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\emp)\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),\Ezero(z_s))\to\mathsf{False})\land
(\hsame(t(\mathsf{append}(\alpha,k)),\Ezero(z_t))\to\mathsf{False})\land\\
(\hsame(s(\mathsf{append}(\alpha,k)),d_s\cdot\Ezero(z_s))\to
\mathsf{False})\land\\
(\hsame(t(\mathsf{append}(\alpha,k)),d_t\cdot\Ezero(z_t))\to
\mathsf{False})\land\\
\forall u',v':\Hist,\,
\bigl(\hsame(s(\mathsf{append}(\alpha,k)),\Eone(u'))\land
\hsame(t(\mathsf{append}(\alpha,k)),\Eone(v'))\bigr)\to\\
\qquad
\mathsf{UnaryHistory}(u')\land
\mathsf{UnaryHistory}(v')\land
\hsame(u,u')\land
\hsame(v,v')\land\\
\qquad
\hsame(u',v)\land
\hsame(u,v').
\end{array}
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:real-unary-streamname-finite-window-selected-e1-tail-coverage-package}
with the displayed histories $z_s,z_t,d_s,d_t$. The resulting witnesses $u$ and
$v$ carry the two selected endpoint displays, the RealUp window classifier row,
the selected RatHistoryClassifier rows, the unary tail rows, the denominator
rows, the endpoint unary rows, the nonempty exclusions, the zero-head
exclusions, and the appended e-zero-tail exclusions.

Now fix arbitrary histories $u',v'$ with the same selected e-one endpoint
displays. Apply
\autoref{thm:real-unary-streamname-finite-window-selected-e1-tail-pairwise-coherence}
with $a=u$, $a'=u'$, $b=v$, and $b'=v'$. The required displayed endpoint
comparisons are exactly the two chosen displays and the two arbitrary displays.

Project the rows supplied by pairwise coherence. They give
$\mathsf{UnaryHistory}(u')$, $\mathsf{UnaryHistory}(v')$, $\hsame(u,u')$,
$\hsame(v,v')$, $\hsame(u',v)$, and $\hsame(u,v')$. Repack this universal
coherence clause after the full coverage rows and package $u,v$ as the displayed
canonical full witnesses.
\end{proof}

Fit. Traditional target: canonical finite-window selected rational endpoint
certificate for RealUp StreamNameUp classifiers. BEDC source:
$\StreamNameUp+\RealUp+\RatUp$ over $\mathsf{BHist}$. Carrier:
$\mathsf{RatStreamNameCarrier}$. Classifier:
$\mathsf{RatStreamNameClassifier}$ through
$\mathsf{RealUnaryStreamWindowClassifier}$. Stability: selected endpoint
$\hsame$ transport plus pairwise e-one tail coherence. Ledger: carrier,
classifier, unary anchor, unary bound, selected offset, selected endpoint
displays, RatHistoryClassifier rows, positive denominator rows, endpoint
unary rows, and endpoint exclusion rows. Core theorem:
\autoref{thm:real-unary-streamname-finite-window-selected-canonical-e1-tail-full-package}.
Exactness: existence, selected endpoint exactness, denominator exclusions,
appended-tail exclusions, and uniqueness up to $\hsame$. Standard bridge: finite
RegSeqRat observation windows. Status: $\mathsf{ProofTarget}$.
