\section{StreamName and RegSeqRat dependency route}
\label{sec:real-streamname-regseqrat-dependency-route}

\begin{theorem}[Real seal StreamName-RegSeqRat dependency route]
\label{thm:real-streamname-regseqrat-dependency-route}
Every $\RealUp$ seal read consumes the finite $\StreamNameUp$ window rows of \autoref{ch:concrete-instances-streamname-namecert} before it reads the regularity and seal rows supplied by \autoref{ch:concrete-instances-regseqrat-namecert}. Thus the real-name carrier is routed through finite scheduled observations and regular rational-source ledgers before any completion-facing consumer can use the $\RealUp$ seal.
\end{theorem}
\begin{proof}
The Real carrier of \autoref{def:real-carrier} is specified as a sealed regular rational stream name. Its observations are StreamName rows, and its regularity certificate is exposed through the RegSeqRat source surface.

Project the StreamName surface first. A finite observation request fixes the scheduled window through \autoref{ch:concrete-instances-streamname-namecert}, so the later seal read cannot introduce an unnamed observation stream.

Then project the RegSeqRat surface. The regularity and classifier rows of \autoref{ch:concrete-instances-regseqrat-namecert} supply the rational-source ledger consumed by the Real seal, so a completion-facing Real read is downstream of both sibling packets.
\end{proof}

\begin{theorem}[Real seal DyadicRatCore-StreamName-RegSeqRat dependency route]
\label{thm:real-dyadic-streamname-regseqrat-dependency-route}
Every accepted current-phase $\RealUp$ seal read factors through the ordered finite route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The DyadicRatCore endpoint and radius ledger is read before the StreamName finite-window schedule, the RegSeqRat regularity and classifier rows, and the local Real seal. The route exports no quotient streams, selected limits, host real equality, ambient completeness, metric-completeness rows, countable choice, or Real completeness coordinate.
\end{theorem}
\begin{proof}
Start from the Real carrier of \autoref{def:real-carrier}. The preceding dependency route, \autoref{thm:real-streamname-regseqrat-dependency-route}, places every Real seal read downstream of the StreamName finite-window rows and the RegSeqRat regular-rational source rows.

Insert the DyadicRatCore face before those rows. The RegSeqRat bridge handoff exactness of \autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness} says that the RegSeqRat finite-window handoff consumes the displayed DyadicRatCore endpoint and radius ledger, while the StreamName four-object terminal pullback of \autoref{thm:streamname-real-completion-four-object-terminal-pullback} keeps the DyadicRatCore, StreamName, RegSeqRat, and local Real faces in one finite terminal packet.

Finally apply Real L10 finite-window witness determinacy, \autoref{thm:real-l10-finite-window-witness-determinacy}. It identifies the public seal boundary with exactly the fused StreamName terminal-window packet, the DyadicRatCore endpoint and radius ledger, the RegSeqRat finite-request section, the local Real seal, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Hence the accepted current-phase seal read has the stated ordered route and none of the excluded quotient, selected-limit, host-equality, completeness, metric-completeness, choice, or Real-completeness coordinates.
\end{proof}

\begin{theorem}[Real L10 four-face route order uniqueness]
\label{thm:real-l10-four-face-route-order-uniqueness}
Every current-phase terminal $\RealUp$ seal section whose displayed rows are the $\DyadicRatCoreUp$ endpoint and radius ledger, the $\StreamNameUp$ finite-window schedule, the $\RegSeqRatUp$ classifier, regularity, and transport rows, and the public $\RealUp$ seal row has
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
as its unique BEDC route. Any attempted route omitting or permuting one face either loses one of the displayed rows or introduces an off-table coordinate, namely quotient stream equality, a selected limit, host real equality, ambient completeness, metric-completeness, countable choice, or a second $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
The forward order is the route of \autoref{thm:real-dyadic-streamname-regseqrat-dependency-route}. It already reads the DyadicRatCore endpoint and radius ledger before the StreamName finite-window schedule, then the RegSeqRat regularity and classifier rows, and finally the local Real seal.

The order of the first three faces cannot be permuted without dropping a displayed row. The DyadicRatCore handoff exactness of \autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness} makes the endpoint and radius ledger the finite handoff read by RegSeqRat, while the StreamName four-object terminal pullback of \autoref{thm:streamname-real-completion-four-object-terminal-pullback} keeps the DyadicRatCore, StreamName, RegSeqRat, and Real faces in one terminal packet.

The public seal boundary is fixed by Real L10 finite-window witness determinacy, \autoref{thm:real-l10-finite-window-witness-determinacy}. RegSeqRat terminal-section exhaustion, \autoref{thm:regseqrat-real-seal-terminal-section-exhaustion}, rules out a fifth-face witness or a shortcut witness between the regular rational section and the Real seal. Therefore every alternative route either omits one of the four displayed faces or leaves the table by adding one of the excluded quotient, selected-limit, host-equality, completeness, choice, or duplicate-seal coordinates.
\end{proof}

\begin{theorem}[Real L10 four-face classifier coherence]
\label{thm:real-l10-four-face-classifier-coherence}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section whose displayed rows are exactly the $\DyadicRatCoreUp$ endpoint and radius ledger, the $\StreamNameUp$ finite-window schedule, the $\RegSeqRatUp$ classifier, regularity, and transport rows, and the public $\RealUp$ seal row. Then the four visible classifier reads of $S$ determine the same finite packet
$$
(\BHist,\hsame,\Cont,\Pkg,\NameCert).
$$
Any classifier disagreement either drops one of the four displayed faces or leaves the table by adding an off-table coordinate: quotient stream equality, a selected limit, host real equality, ambient completeness, metric-completeness, countable choice, or a duplicate $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
Start with the ordered route of \autoref{thm:real-l10-four-face-route-order-uniqueness}. It fixes the only current-phase terminal order as $\DyadicRatCoreUp$ to $\StreamNameUp$ to $\RegSeqRatUp$ to $\RealUp$, so a visible classifier comparison must be read on those four faces and on no independent route.

The endpoint and radius classifier compatibility comes from \autoref{thm:dyadicratcore-regseqrat-bridge-handoff-exactness}. The finite-window packet shared by the four faces is supplied by \autoref{thm:streamname-real-completion-four-object-terminal-pullback}. Together these two results place the DyadicRatCore ledger, StreamName schedule, RegSeqRat classifier rows, and local Real seal row on one finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support packet.

It remains to exclude extra classifier sources. RegSeqRat terminal-section exhaustion, \autoref{thm:regseqrat-real-seal-terminal-section-exhaustion}, rules out a shortcut from the regular rational section to the Real seal and rules out a fifth classifier face. Real L10 finite-window witness determinacy, \autoref{thm:real-l10-finite-window-witness-determinacy}, then fixes the public seal boundary to the same finite-window witness. Hence any classifier mismatch is visible as the loss of one of the four displayed faces, or else it requires one of the listed off-table coordinates.
\end{proof}

\begin{theorem}[Real L10 route face deletion obstruction]
\label{thm:real-l10-route-face-deletion-obstruction}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section with public seal boundary displayed on
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp .
$$
Then no route presenting the same public boundary may delete any one of these four faces. Deleting $\DyadicRatCoreUp$ loses the endpoint and radius ledger rows, deleting $\StreamNameUp$ loses the finite-window schedule, deleting $\RegSeqRatUp$ loses the regularity and classifier rows, and deleting $\RealUp$ loses the seal row itself. Any purported route retaining the boundary after such a deletion must leave the permitted current-phase surface by adding quotient stream equality, a selected limit, host real equality, ambient completeness, metric-completeness, countable choice, or a duplicate $\RealUp$ seal coordinate.
\end{theorem}
\begin{proof}
The accepted boundary first has the ordered route of \autoref{thm:real-dyadic-streamname-regseqrat-dependency-route}. Its unique current-phase order is fixed by \autoref{thm:real-l10-four-face-route-order-uniqueness}, so any route with the same public boundary must read the four displayed faces in the same finite order.

Now compare the four deletions. Without $\DyadicRatCoreUp$ the route has no endpoint and radius ledger feeding the rational source rows. Without $\StreamNameUp$ it has no finite-window schedule. Without $\RegSeqRatUp$ it has no regularity and classifier surface between the scheduled observations and the seal. Without $\RealUp$ it has no public seal row.

The terminal packet cannot hide these losses in another current-phase coordinate. The StreamName terminal pullback of \autoref{thm:streamname-real-completion-four-object-terminal-pullback} keeps the four faces in one finite terminal packet, while \autoref{thm:regseqrat-real-seal-terminal-section-exhaustion} rules out a shortcut or fifth face between the regular rational section and the Real seal.

Finally apply the classifier coherence theorem, \autoref{thm:real-l10-four-face-classifier-coherence}. It says the visible classifier reads determine the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet exactly on these faces; hence a route that claims the same boundary after deleting one face must supply the missing row by one of the excluded off-table coordinates.
\end{proof}

\begin{theorem}[Real L10 four-face local-threshold descent]
\label{thm:real-l10-four-face-local-threshold-descent}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion packet displayed exactly on the four faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
with support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. If $\mathcal E$ satisfies the current-phase local threshold, then every accepted projection of the four-face route carries the same objectwise local threshold records on the DyadicRatCore endpoint and radius ledger, the StreamName finite-window schedule, the RegSeqRat classifier and regularity rows, and the local Real seal row.

Conversely, any accepted four-face route projection carrying those four local threshold records together with the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support repacks as the current-phase Phase $\RealUp$ and Completion exit certificate of \autoref{thm:real-l10-current-phase-exit-local-threshold}. The descent and repacking use no quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First put all classifier reads on one finite packet. By \autoref{thm:real-l10-four-face-classifier-coherence}, the visible classifier coordinates of an accepted route projection over the four displayed faces determine the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support packet.

For descent, apply \autoref{thm:real-l10-current-phase-exit-local-threshold}. It identifies the current Phase Real and Completion exit criterion with the objectwise product of the four local threshold records on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, supported by exactly those finite rows. Hence every accepted projection of that same packet reads the same four local threshold records.

The projection order does not add a second certificate. Use \autoref{thm:real-l10-four-face-route-order-uniqueness} to fix the terminal route and use \autoref{thm:real-l10-face-order-permutation-invariance} to compare support-row-preserving projections of the displayed packet. Thus the descended local threshold is independent of the accepted projection order.

For the converse direction, start with an accepted four-face route projection carrying the four local threshold records and the same displayed support rows. The local-threshold theorem repacks these rows as the current-phase exit certificate, and the classifier coherence theorem keeps the repacked certificate on the same finite four-face packet.

Finally apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Each face record and each displayed support row is indispensable, so no shortened route or off-table coordinate can present the same exit certificate. Therefore the repacking uses exactly the stated four faces and excludes the listed quotient, selected-limit, host-equality, choice, metric-completeness, aggregate-status, aggregate-bridge, standard-bridge, and completeness data.
\end{proof}

\begin{theorem}[Real L10 tail-budget projection nonescape]
\label{thm:real-l10-tail-budget-projection-nonescape}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section whose public seal is read by a $\RegSeqRatUp$ tail-budget consumer. Then every support-row-preserving projection of that consumer remains on the displayed four-face route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The projection preserves the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows, and it may read only the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat tail-budget classifier and regularity rows, and the terminal Real seal. No such projection may introduce quotient stream equality, selected limits, host real equality, countable choice, ambient completeness, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or a $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First lock the tail-budget consumer to its source route. Apply \autoref{thm:regseqrat-tail-budget-real-seal-nonescape}. The consumer can read the Real seal only through the StreamName schedule, the DyadicRatCore tolerance row, the RegSeqRat classifier, and the terminal $\RealUp$ seal. Thus the read has no source for quotient stream equality, selected limits, host real equality, choice, completeness data, or a separate Real completeness coordinate.

Next identify the local threshold records on the same four faces. Apply \autoref{thm:real-l10-four-face-local-threshold-descent}. The accepted projection is therefore read objectwise on the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier and regularity rows, and the local Real seal row, while preserving the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support packet.

It remains to exclude alternative projections of that packet. Use \autoref{thm:real-l10-face-order-permutation-invariance} to compare support-row-preserving reads of the displayed route, and then apply \autoref{thm:real-l10-exit-certificate-face-minimality}. The first result prevents a reordered projection from changing the certificate, and the second makes every listed face and support row indispensable. Hence a projection that is shortened or enlarged cannot present the same current-phase Real seal read, so the only surviving route is the displayed four-face route with exactly the support rows named in the statement.
\end{proof}

\begin{theorem}[Real L10 four-face support exhaustion]
\label{thm:real-l10-four-face-support-exhaustion}
Every accepted current-phase terminal $\RealUp$ seal section on the route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
has exactly the visible support inventory consisting of the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the terminal Real seal, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Conversely, that inventory repacks as the same current-phase Phase $\RealUp$ and Completion exit certificate. It contains no quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First read the objectwise threshold rows. Apply \autoref{thm:real-l10-four-face-local-threshold-descent}: the accepted terminal section carries the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier and regularity rows, and the local Real seal row over the common $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support packet.

Next lock that packet to the route. By \autoref{thm:real-l10-tail-budget-projection-nonescape}, every support-row-preserving projection remains on
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
The route therefore has no available coordinate outside the four construction faces and the displayed support rows.

Now identify the endpoint and schedule inventories. Apply \autoref{thm:dyadicratcore-l10-exit-ledger-consumer-normal-form} to read the DyadicRatCore endpoint and tolerance ledger, and apply \autoref{thm:streamname-terminal-four-face-support-exhaustion} to read the StreamName-side finite-window support surface. These two inventories sit inside the same RegSeqRat classifier, regularity, and transport rows and the same terminal Real seal.

For the converse, use \autoref{thm:real-l10-exit-certificate-face-minimality}. The listed four face records and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are indispensable, so the inventory repacks as the same current-phase Phase $\RealUp$ and Completion exit certificate. The same minimality statement excludes quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 four-face exit criterion equivalence]
\label{thm:real-l10-four-face-exit-criterion-equivalence}
An accepted current-phase terminal $\RealUp$ seal section satisfies the Phase $\RealUp$ and Completion exit criterion if and only if the same finite support packet exposes exactly the $\DyadicRatCoreUp$ endpoint and tolerance ledger, the $\StreamNameUp$ finite-window schedule, the $\RegSeqRatUp$ classifier, regularity, and transport rows, the local $\RealUp$ seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Equivalently, the exit criterion is the four-face packet
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
with no quotient streams, selected limits, host real equality, countable choice, ambient completeness, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or separate $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
For the forward direction, apply \autoref{thm:real-l10-four-face-support-exhaustion}. It identifies every accepted terminal seal section on the displayed route with the visible inventory consisting of the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the terminal Real seal, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

For the reverse direction, first read the objectwise exit ledger through \autoref{thm:dyadicratcore-phase-real-completion-objectwise-exit-equivalence}. Then use \autoref{thm:streamname-terminal-four-face-support-exhaustion} for the finite-window schedule and support surface, \autoref{thm:regseqrat-real-terminal-four-face-exactness} for the RegSeqRat terminal classifier and regularity rows, and \autoref{thm:regseqrat-four-face-finite-cover-normal-form} for the finite-cover normal form joining the four faces.

These ingredients repack the displayed support inventory as the current-phase Phase $\RealUp$ and Completion exit certificate. Finally, \autoref{thm:real-l10-dependency-route-axis-independence} separates that certificate from aggregate formalstatus, leantarget, bridge, metric-completeness, selected-limit, quotient-stream, and separate $\RealUp$ completeness coordinates, so the equivalence has exactly the exclusion list stated above.
\end{proof}

\begin{theorem}[Real L10 dependency route axis independence]
\label{thm:real-l10-dependency-route-axis-independence}
For any accepted current-phase terminal $\RealUp$ seal section on the route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp ,
$$
the dependency route determines only the construction faces, the classifier faces, and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. It does not determine or aggregate any $\formalstatus$, $\leantarget$, or $\bridgestatus$ row, nor any standard bridge row, metric-completeness row, selected limit, quotient stream, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First identify the route and the support packet. The dependency theorem \autoref{thm:real-dyadic-streamname-regseqrat-dependency-route} fixes the ordered four-object route, and \autoref{thm:real-l10-four-face-local-threshold-descent} reads the accepted local-threshold records on exactly those four faces with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Next rule out escape through tail-budget projection. Apply \autoref{thm:real-l10-tail-budget-projection-nonescape}. Any support-row-preserving consumer remains on the same four-face route and has no coordinate for quotient stream equality, selected limits, host real equality, countable choice, ambient completeness, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or a $\RealUp$ completeness row.

Finally separate the route data from the verification and bridge axes. Apply \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}. These keep status, Lean-target, and bridge-status rows as face-local reports rather than route-level credentials. Therefore the route supplies construction and classifier evidence with its finite support rows, but it supplies no aggregate verification token, bridge credential, metric-completeness claim, selected limit, quotient stream, or $\RealUp$ completeness claim.
\end{proof}

\begin{theorem}[Real L10 completeness-coordinate refusal]\label{thm:real-l10-completeness-coordinate-refusal}
Every accepted current-phase terminal $\RealUp$ seal section satisfying the four-face Phase $\RealUp$ and Completion exit criterion has no BEDC coordinate for Real completeness, metric completeness, selected limits, quotient stream equality, host real equality, countable choice, aggregate $\formalstatus$, or aggregate $\bridgestatus$.

Equivalently, any assertion of one of these coordinates is not a refinement of the current L10 exit surface. It leaves the finite support packet
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
and is therefore a claim outside the accepted current-phase terminal seal.
\end{theorem}
\begin{proof}
First apply \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. It identifies the exit criterion with the finite packet whose only construction faces are the $\DyadicRatCoreUp$ endpoint and tolerance ledger, the $\StreamNameUp$ finite-window schedule, the $\RegSeqRatUp$ classifier, regularity, and transport rows, the local $\RealUp$ seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next apply \autoref{thm:real-l10-four-face-support-exhaustion}. The visible inventory of an accepted terminal section is exhausted by those four faces and support rows. Thus there is no remaining BEDC coordinate in the packet for quotient stream equality, selected limits, host real equality, countable choice, metric completeness, aggregate status, aggregate bridge data, or separate $\RealUp$ completeness.

It remains to rule out the same coordinates after projection. Use \autoref{thm:real-l10-tail-budget-projection-nonescape}. Any support-row-preserving consumer remains on the displayed route and cannot manufacture a new completion, limit-selection, quotient, host-equality, choice, status, bridge, or Real-completeness coordinate.

Finally apply \autoref{thm:real-l10-dependency-route-axis-independence}. The construction route is independent of the verification and bridge axes, so aggregate $\formalstatus$ and $\bridgestatus$ rows cannot be recovered from the terminal seal. Hence any assertion of one of the listed coordinates leaves the current L10 exit surface rather than strengthening it.
\end{proof}

\begin{theorem}[Real L10 four-face exit certificate rigidification]
\label{thm:real-l10-four-face-exit-certificate-rigidification}
An accepted current-phase terminal $\RealUp$ seal section is a Phase $\RealUp$ and Completion exit certificate if and only if its visible packet is the four-face route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
with the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the terminal Real seal, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Any presentation with the same exit certificate preserves those four faces and support rows. It cannot add quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge data, standard bridge data, or a separate $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First identify the certificate. Apply \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. It says that the Phase $\RealUp$ and Completion exit criterion is exactly the finite packet displayed on the four construction faces with the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Next exhaust the support. Apply \autoref{thm:real-l10-four-face-support-exhaustion}. The accepted terminal seal section has no visible support beyond the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the terminal Real seal, and the named shared rows.

Now rigidify alternative presentations of the same certificate. Use \autoref{thm:real-l10-four-face-route-order-uniqueness}, \autoref{thm:real-l10-four-face-classifier-coherence}, and \autoref{thm:real-l10-exit-certificate-face-minimality}. These results keep the route order, classifier packet, and indispensable face records fixed, so a second presentation cannot delete, permute, duplicate, or replace one of the displayed faces while preserving the same exit certificate.

Finally apply \autoref{thm:real-l10-dependency-route-axis-independence} and \autoref{thm:real-l10-completeness-coordinate-refusal}. The route supplies construction and classifier evidence only, and the current L10 exit surface has no coordinate for quotient streams, selected limits, host real equality, countable choice, metric completeness, aggregate status, aggregate bridge data, standard bridge data, or separate $\RealUp$ completeness. Hence every presentation of the same exit certificate is rigidly the displayed four-face packet with the named support rows.
\end{proof}

\begin{theorem}[Real L10 facewise projection gluing]
\label{thm:real-l10-facewise-projection-gluing}
Let an accepted current-phase terminal $\RealUp$ seal section carry four facewise projections on
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Assume the projections preserve the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the local Real seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Then their common read glues to the same Phase $\RealUp$ and Completion exit certificate.

The glued certificate has no quotient stream, selected limit, host equality, countable choice, metric-completeness data, aggregate status, aggregate bridge data, standard bridge data, or separate $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First read the facewise data through \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. Since each projection preserves the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, and the local Real seal row over the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support, each face presents the finite packet required by the Phase $\RealUp$ and Completion exit criterion.

Next identify the common support. Apply \autoref{thm:real-l10-four-face-support-exhaustion}. The accepted terminal seal has no visible construction support outside the four displayed faces and the named support rows, so the four preserved reads cannot require an additional completion, quotient, equality, choice, status, or bridge coordinate.

Now align the classifier and route data. Use \autoref{thm:real-l10-four-face-classifier-coherence} to keep the RegSeqRat classifier, regularity, and transport rows coherent across the four projections. Then use \autoref{thm:real-l10-exit-certificate-face-minimality} to repack the preserved endpoint, schedule, classifier, transport, and seal rows as one indispensable four-face certificate rather than four unrelated fragments.

Finally exclude escape coordinates. Apply \autoref{thm:real-l10-dependency-route-axis-independence} to separate the construction route from aggregate status, Lean-target, and bridge rows, and apply \autoref{thm:real-l10-completeness-coordinate-refusal} to rule out Real completeness, metric completeness, selected limits, quotient streams, host equality, and countable choice. Therefore the common read of the four support-preserving projections glues to exactly the same current-phase Phase $\RealUp$ and Completion exit certificate, with no extra coordinate beyond the displayed packet.
\end{proof}

\begin{theorem}[Real terminal seal machine-route exhaustion]
\label{thm:real-terminal-seal-machine-route-exhaustion}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section on
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Then the machine-facing support of $S$ is exhausted by exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff. These three touchpoints consume the same four-face certificate glued from the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the terminal Real seal, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

No machine-facing route for $S$ may add quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or a $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First glue the Real-side certificate. Apply \autoref{thm:real-l10-facewise-projection-gluing}. The four support-preserving projections on the displayed route have a common read as the same Phase $\RealUp$ and Completion exit certificate, and the glued certificate already excludes quotient streams, selected limits, host equality, countable choice, metric-completeness data, aggregate status, aggregate bridge data, standard bridge data, and separate $\RealUp$ completeness.

Next identify the certificate with the local exit criterion. Apply \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. The glued Real certificate is exactly the finite packet consisting of the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the local Real seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Now bind that finite packet to the machine route. Use \autoref{thm:streamname-open-phase-lean-touchpoint-triad} and \autoref{thm:streamname-real-completion-exit-lean-route-boundary}. These identify the machine-facing route of the same four-face exit read with exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

Finally apply \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}. The DyadicRatCore-side ledger theorem says that an accepted four-face Phase Real and Completion packet has no machine support outside those three route sites. Hence the terminal $\RealUp$ seal section consumes precisely the three named touchpoints, while all quotient-stream, selected-limit, host-equality, choice, metric-completeness, aggregate-status, aggregate-bridge, standard-bridge, and $\RealUp$ completeness coordinates remain outside the accepted current-phase route.
\end{proof}

\begin{theorem}[Real four-face machine touchpoint minimality]
\label{thm:real-four-face-machine-touchpoint-minimality}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section on
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Then $S$ is machine-admissible for the Phase $\RealUp$ and Completion exit if and only if the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff read the same four-face certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Moreover these three touchpoints are a minimal basis for the accepted machine-facing route: deleting any one of them fails to present the same accepted route from the DyadicRatCore endpoint and tolerance ledger through the StreamName finite-window schedule and the RegSeqRat classifier, regularity, and transport rows to the terminal Real seal.
\end{theorem}
\begin{proof}
For the forward direction, apply \autoref{thm:real-terminal-seal-machine-route-exhaustion}. The theorem identifies the machine-facing support of $S$ with exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff, all consuming the same four-face certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

For the reverse direction, use \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. A common read by the three named machine touchpoints exposes precisely the finite support packet for the Phase $\RealUp$ and Completion exit criterion. Then apply \autoref{thm:streamname-real-completion-exit-lean-route-boundary} and \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}: the StreamName boundary theorem places the read on the same machine-facing route, and the DyadicRatCore completeness theorem rules out any additional machine support site.

It remains to prove minimality. The StreamName singleton finite-window handoff is required by \autoref{thm:streamname-open-phase-lean-touchpoint-triad}; without it the finite-window schedule is absent from the machine read. The DyadicRatCore RegSeqRat bridge handoff exactness is required by \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}; without it the endpoint and tolerance ledger do not reach the RegSeqRat classifier and transport rows. The RegSeqRat Real seal handoff is required by \autoref{thm:streamname-real-completion-exit-lean-route-boundary}; without it the route has no terminal $\RealUp$ seal presentation.

Finally apply \autoref{thm:real-l10-route-face-deletion-obstruction}. Deleting any indispensable construction face or support row from the four-face packet fails to present the same accepted exit certificate. Therefore deleting any one of the three machine touchpoints fails to present the same accepted machine-facing route, and the three touchpoints form the minimal sufficient basis for admissibility.
\end{proof}

\begin{theorem}[Real L10 finite bundle induction]
\label{thm:real-l10-finite-bundle-induction}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section over the ordered route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Let $\mathcal B$ be a finite $\mathsf{ProbeBundle}$ of certified unary observations for $S$. Assume that the rows of $\mathcal B$ expose exactly the DyadicRatCore endpoint and tolerance ledger, the StreamName finite-window schedule, the RegSeqRat classifier, regularity, and transport rows, the local Real seal row, and the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Then induction over the rows of $\mathcal B$ determines a unique terminal four-face audit packet for $S$, and that packet is precisely the packet consumed by the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff of \autoref{thm:real-four-face-machine-touchpoint-minimality}. The induced packet contains no quotient stream equality, selected limit, host real equality, countable-choice row, metric-completeness datum, aggregate formalstatus row, aggregate bridge row, standard bridge row, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the empty prefix of $\mathcal B$. The visible support is the fixed ordered route of \autoref{thm:real-l10-four-face-route-order-uniqueness}, so the prefix has no alternative route on which to place a hidden quotient, selected-limit, host-equality, choice, completeness, status, or bridge coordinate.

For the induction step, add one certified unary observation while preserving the same visible support rows. Apply \autoref{thm:real-l10-four-face-classifier-coherence}: the new observation must read the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet as the earlier rows, and its RegSeqRat classifier, regularity, and transport data cannot split away from the DyadicRatCore ledger, StreamName schedule, or local Real seal.

It remains to rule out a step that changes the terminal packet by deleting or replacing a face. Use \autoref{thm:real-l10-route-face-deletion-obstruction}. Any such change loses one of the four displayed construction faces or supplies the missing row from an off-table coordinate, which contradicts the hypothesis that $\mathcal B$ exposes exactly the displayed ledger, schedule, classifier, regularity, transport, seal, and shared support rows.

After the finite induction closes, identify the resulting packet with the machine-facing route. Apply \autoref{thm:streamname-real-completion-exit-lean-route-boundary} and \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}. These boundary theorems place the induced four-face packet on exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff.

Finally invoke \autoref{thm:real-four-face-machine-touchpoint-minimality}. Since those three touchpoints are the minimal basis for the accepted route, the packet determined by the finite bundle is the unique terminal four-face audit packet consumed by them, and the excluded quotient-stream, selected-limit, host-equality, choice, metric-completeness, aggregate-status, aggregate-bridge, standard-bridge, and $\RealUp$ completeness coordinates remain outside the accepted current-phase surface.
\end{proof}

\begin{theorem}[Real L10 machine-audit locality]
\label{thm:real-l10-machine-audit-locality}
Let $S$ be an accepted current-phase terminal $\RealUp$ seal section on
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Assume that the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff read the same four-face certificate named in \autoref{thm:real-four-face-machine-touchpoint-minimality}. Then every audit-facing coordinate of that machine read is exactly one of the four local face records: the local closurestatus, formalstatus, leantarget, and bridgestatus records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ seal face.

Conversely, those four local objectwise audit records together with the three named machine touchpoints present the same machine-audit route for $S$. The route contains no aggregate formalstatus row, route-level leantarget, aggregate bridge row, standard bridge row, quotient stream equality, selected limit, countable-choice row, metric-completeness datum, or $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
First identify the machine route. Apply \autoref{thm:real-terminal-seal-machine-route-exhaustion} and \autoref{thm:real-four-face-machine-touchpoint-minimality}. The accepted terminal seal has exactly the three machine touchpoints in the statement, and those touchpoints consume one common four-face certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next read the audit records objectwise. Use \autoref{thm:real-l10-face-leantarget-noncollapse} and \autoref{thm:real-l10-terminal-four-face-status-locality}. These keep closurestatus, formalstatus, leantarget, and bridgestatus attached to the four local faces, so the machine read cannot fuse them into a route-level verification token or replace a local face record by an aggregate bridge credential.

Now separate the gateway inventory from the touchpoint inventory. Apply \autoref{thm:streamname-real-completion-gateway-face-record-noncollapse} and \autoref{thm:streamname-real-completion-gateway-touchpoint-factorization}. The gateway audit records are the four objectwise face records, while the machine-facing route factors through the three named handoff positions. Thus a touchpoint reports its route position only by reading those local records; it does not create an additional audit-facing coordinate.

For the converse direction, start with the four local closurestatus, formalstatus, leantarget, and bridgestatus records together with the three touchpoints. The gateway factorization theorem repacks them as the same four-face machine read, and the terminal seal exhaustion theorem identifies that read with the accepted route for $S$.

Finally close the exclusions. Use \autoref{thm:streamname-open-phase-lean-touchpoint-triad}, \autoref{thm:streamname-real-completion-exit-lean-route-boundary}, and \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}. These boundary results exhaust the current machine support by the three named touchpoints and leave no coordinate for aggregate formalstatus, route-level leantarget, aggregate bridge data, standard bridge data, quotient stream equality, selected limits, countable choice, metric completeness, or separate $\RealUp$ completeness.
\end{proof}
