\begin{theorem}[Real stream prefix tail endpoint projection]
\label{thm:real-stream-prefix-tail-endpoint-projection}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$ and indices $n,m$,
if the prefix through $n$ is classified and every endpoint along the finite
tail of length $m$ is rational-history classified, then the selected tail
endpoint is rational-history classified:
$$
\mathsf{RealStreamPrefixClassifier}(x,y,n)\land
\bigl(\forall k,\ 1\le k\le m\Longrightarrow
\mathsf{RatHistoryClassifier}(x(n+k),y(n+k))\bigr)
\Longrightarrow
\mathsf{RatHistoryClassifier}(x(n+m),y(n+m)).
$$
Ten-field fit: traditional target finite RealUp prefix endpoint readback; BEDC
source RealUp stream prefixes over RatUp point classifiers; carrier
rational-observation streams; classifier
$\mathsf{RealStreamPrefixClassifier}$; stability by tail extension and endpoint
projection; ledger initial prefix length, tail length, and selected endpoint;
core theorem this projection; exactness selected endpoint classification;
standard bridge RegSeqRat finite observation readback; status
$\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-stream-prefix-classifier-tail-extension} to the
classified prefix through $n$ and the finite tail endpoint hypothesis. This
gives $\mathsf{RealStreamPrefixClassifier}(x,y,n+m)$.

Now apply \autoref{thm:real-stream-prefix-classifier-endpoint} at the endpoint
index $n+m$. The resulting projection is exactly
$\mathsf{RatHistoryClassifier}(x(n+m),y(n+m))$.
\end{proof}

\begin{theorem}[Real stream prefix truncated endpoint common e-one tail readback]
\label{thm:real-stream-prefix-truncated-endpoint-common-e1-tail-readback}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$ and indices $m,n$,
if $\mathsf{RealStreamPrefixClassifier}(x,y,m+n)$ holds, then the endpoint at
$n$ has a common e-one tail readback:
$$
\exists a,b,\ \hsame(x(n),\Eone(a))\land \hsame(y(n),\Eone(b))\land
\mathsf{UnaryHistory}(a)\land \mathsf{UnaryHistory}(b)\land \hsame(a,b).
$$
\end{theorem}
\begin{proof}
Truncate the displayed prefix classifier to the selected endpoint $n$ and use
the denominator package there. Its positive unary denominator rows give unary
endpoint witnesses and separate both selected endpoints from $\emp$, so unary
nonempty readback exposes e-one tails $a$ and $b$. The truncated e-one pair
readback theorem then returns the two unary tail rows and their $\hsame$
comparison.
\end{proof}
\leanchecked{BEDC.Derived.RealUp.RealStreamPrefixClassifier\_truncated\_endpoint\_common\_e1\_tail\_readback}

\begin{theorem}[Real stream prefix probe endpoint determinacy]
\label{thm:real-stream-prefix-probe-endpoint-determinacy}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, let
$\mathcal P$ be a finite certified $\mathsf{ProbeBundle}$ window and let
$n$ be a unary observation with $\mathsf{InBundle}(n,\mathcal P)$. Suppose the
window supplies $\mathsf{RealStreamPrefixClassifier}(x,y,n)$ and, for every
displayed tail row selected by $\mathcal P$ after $n$, the finite row
$\mathsf{RatHistoryClassifier}(x(n+k),y(n+k))$ is present. Then every consumer
endpoint selected from $\mathcal P$ has a unique
$\mathsf{RatHistoryClassifier}$ readback, and its endpoint admits the same
common e-one tail witness after $\hsame$ transport:
$$
\mathsf{InBundle}(n,\mathcal P)\Longrightarrow
\forall j,\ \mathsf{InBundle}(j,\mathcal P)\Longrightarrow
\exists a,b,\ \hsame(x(j),\Eone(a))\land \hsame(y(j),\Eone(b))\land
\mathsf{UnaryHistory}(a)\land \mathsf{UnaryHistory}(b)\land \hsame(a,b).
$$
The statement reads only the displayed finite rows of $\mathcal P$; no
observation outside the certified probe window is used.
\end{theorem}
\begin{proof}
Restrict the finite $\mathsf{ProbeBundle}$ to the selected prefix through $n$
and to the displayed consumer endpoint $j$. The membership rows
$\mathsf{InBundle}(n,\mathcal P)$ and $\mathsf{InBundle}(j,\mathcal P)$ are
exactly the evidence that these two observations lie inside the certified
window.

Apply \autoref{thm:real-stream-prefix-tail-endpoint-projection} to the selected
prefix and the finite tail rows displayed by $\mathcal P$. This gives the
endpoint $\mathsf{RatHistoryClassifier}$ readback for the consumer endpoint,
and uniqueness follows because the readback is selected from the same finite
bundle row rather than from an external observation.

Finally apply
\autoref{thm:real-stream-prefix-truncated-endpoint-common-e1-tail-readback} to
the resulting classified prefix. The $\hsame$ transport keeps the two endpoint
histories in the same rational-observation class, so the e-one tail witnesses
are the common tail witnesses recorded by the finite probe window.
\end{proof}

\begin{theorem}[Real stream prefix two-probe endpoint coherence]
\label{thm:real-stream-prefix-two-probe-endpoint-coherence}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, let
$\mathcal P$ and $\mathcal Q$ be finite certified $\mathsf{ProbeBundle}$
windows. Suppose the same unary observation $j$ satisfies
$\mathsf{InBundle}(j,\mathcal P)$ and $\mathsf{InBundle}(j,\mathcal Q)$, and
suppose both windows supply the $\mathsf{RealStreamPrefixClassifier}$ row and
the finite $\mathsf{RatHistoryClassifier}$ tail rows required by
\autoref{thm:real-stream-prefix-probe-endpoint-determinacy} for the selected
endpoint $j$. Then the endpoint readbacks
$\mathsf{RatHistoryClassifier}(x(j),y(j))$ obtained through $\mathcal P$ and
through $\mathcal Q$ are the same up to $\hsame$, and their common e-one tail
witnesses agree up to $\hsame$ transport:
$$
\begin{aligned}
&\mathsf{InBundle}(j,\mathcal P)\land
\mathsf{InBundle}(j,\mathcal Q) \\
&\qquad \text{and the two displayed endpoint-determinacy packets at } j \\
&\qquad \text{determine histories } a_{\mathcal P},b_{\mathcal P},
a_{\mathcal Q},b_{\mathcal Q} \text{ with} \\
&\qquad \hsame(a_{\mathcal P},a_{\mathcal Q})\land
\hsame(b_{\mathcal P},b_{\mathcal Q})\land
\hsame(x(j),\Eone(a_{\mathcal P}))\land
\hsame(x(j),\Eone(a_{\mathcal Q})) \\
&\qquad \land\ \hsame(y(j),\Eone(b_{\mathcal P}))\land
\hsame(y(j),\Eone(b_{\mathcal Q})).
\end{aligned}
$$
Ten-field fit: traditional target finite RealUp two-window endpoint coherence;
BEDC source RealUp stream prefixes over RatUp point classifiers; carrier the
two certified $\mathsf{ProbeBundle}$ windows over the same streams; classifier
$\mathsf{RealStreamPrefixClassifier}$ at the selected unary observation;
stability by $\hsame$ transitivity across the two endpoint readbacks; ledger
the two window memberships, prefix classifiers, tail rows, endpoint row, and
common e-one witnesses; core theorem this two-probe coherence statement;
exactness the fixed endpoint row $j$; standard bridge StreamName and RegSeqRat
finite observation readback; status $\mathsf{ProofTarget}$. No observation
outside the two certified probe windows is used.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-stream-prefix-probe-endpoint-determinacy} to
$\mathcal P$ at the selected observation $j$. The window membership row and
the displayed classifier and tail rows return the endpoint
$\mathsf{RatHistoryClassifier}(x(j),y(j))$ together with common e-one tail
witnesses $a_{\mathcal P}$ and $b_{\mathcal P}$.

Apply the same theorem to $\mathcal Q$ at the same selected observation $j$.
This gives the endpoint readback through the second finite window and common
e-one tail witnesses $a_{\mathcal Q}$ and $b_{\mathcal Q}$.

Both applications read the fixed endpoint row $j$ of the same streams $x$ and
$y$. Transitivity of $\hsame$ identifies the two rational endpoint readbacks,
and the same transport identifies the e-one tail witnesses. Since every row
used in the argument is selected from either $\mathcal P$ or $\mathcal Q$, no
external observation enters the comparison.
\end{proof}

\begin{theorem}[Real stream prefix probe-union endpoint readback]
\label{thm:real-stream-prefix-probe-union-endpoint-readback}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, let
$\mathcal P$ and $\mathcal Q$ be finite certified $\mathsf{ProbeBundle}$
windows, and let $\mathcal U$ be their synchronized union window certified by
\autoref{thm:streamname-synchronized-window-union-carrier}. Suppose each source
window supplies the $\mathsf{RealStreamPrefixClassifier}$ rows and finite
$\mathsf{RatHistoryClassifier}$ tail rows required by
\autoref{thm:real-stream-prefix-probe-endpoint-determinacy}. Then every unary
endpoint $j$ selected by either source window has the same
$\mathsf{RatHistoryClassifier}(x(j),y(j))$ readback through the union window
$\mathcal U$, and the common e-one tail witnesses displayed by the source
window and by $\mathcal U$ agree by $\hsame$ transport.

Equivalently, if
$\mathsf{InBundle}(j,\mathcal P)\lor\mathsf{InBundle}(j,\mathcal Q)$, then
$\mathsf{InBundle}(j,\mathcal U)$ and the union read supplies histories
$a_{\mathcal U},b_{\mathcal U}$ with
$$
\hsame(x(j),\Eone(a_{\mathcal U}))\land
\hsame(y(j),\Eone(b_{\mathcal U}))\land
\mathsf{UnaryHistory}(a_{\mathcal U})\land
\mathsf{UnaryHistory}(b_{\mathcal U}).
$$
If $j$ lies in both $\mathcal P$ and $\mathcal Q$, these witnesses are
$\hsame$-identified with the two source-window witnesses of
\autoref{thm:real-stream-prefix-two-probe-endpoint-coherence}; if $j$ lies in
only one source window, the union read is the unique displayed readback of that
source window.

Ten-field fit: traditional target finite RealUp union endpoint readback; BEDC
source RealUp stream prefixes with RatUp point classifiers; carrier the
certified $\mathsf{ProbeBundle}$ union membership rows for
$\mathcal P,\mathcal Q,\mathcal U$; classifier
$\mathsf{RealStreamPrefixClassifier}$ at the displayed unary prefix; stability
by $\hsame$ transport of the e-one tails; ledger the finite endpoint ledger,
source memberships, synchronized union membership, prefix classifiers, and
tail rows; core theorem this probe-union readback statement; exactness the
fixed finite endpoint row $j$; bridge data the StreamName synchronized-window
union coverage and RegSeqRat finite observation readback; status
$\mathsf{ProofTarget}$. No quotient-real equality, completeness theorem, or
host real comparison is used.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-synchronized-window-union-carrier} to the two
certified probe windows. It places every endpoint selected by $\mathcal P$ or
by $\mathcal Q$ into the synchronized union window $\mathcal U$ and records the
finite union membership row used by the later readback.

When the selected endpoint lies only in $\mathcal P$, apply
\autoref{thm:real-stream-prefix-probe-endpoint-determinacy} to
$\mathcal P$. The union membership supplied by the synchronized carrier reads
the same finite endpoint row, so the union readback is the displayed
$\mathcal P$ readback transported along $\hsame$.

The case where the endpoint lies only in $\mathcal Q$ is identical, with
$\mathcal Q$ supplying the source readback and the union carrier supplying the
same endpoint row in $\mathcal U$.

If the endpoint lies in both source windows, first apply endpoint determinacy
in each window, then apply
\autoref{thm:real-stream-prefix-two-probe-endpoint-coherence}. The coherence
row identifies the two rational endpoint readbacks and transports the common
e-one tail witnesses through $\hsame$, so the union read has the same displayed
tails.

All rows consumed by the argument are finite rows of the two source probe
windows or of their synchronized union. Hence the endpoint readback remains a
RegSeqRat-style finite observation read and never appeals to a quotient real,
completeness principle, or host equality.
\end{proof}

\begin{theorem}[Real stream prefix probe-union terminal four-face factorization]
\label{thm:real-stream-prefix-probe-union-terminal-four-face-factorization}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, let
$\mathcal P$ and $\mathcal Q$ be finite certified $\mathsf{ProbeBundle}$
windows and let $\mathcal U$ be their synchronized union window. Suppose the
two source windows supply the $\mathsf{RealStreamPrefixClassifier}$ rows and
finite $\mathsf{RatHistoryClassifier}$ tail rows required by
\autoref{thm:real-stream-prefix-probe-union-endpoint-readback}. Then every
endpoint readback selected from $\mathcal U$ factors through exactly one
terminal four-face packet over
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$.

The packet has precisely the displayed rows
$$
\begin{gathered}
\mathsf{BHist}\text{-indexed finite probe histories},\quad
\hsame\text{-transport for endpoint tails},\quad
\Cont\text{-continuity rows},\\
\Pkg\text{-package rows for the synchronized union window},\quad
\NameCert\text{-certification rows for the four visible faces}.
\end{gathered}
$$
Its $\StreamNameUp$ face is the synchronized carrier $\mathcal U$, its
$\DyadicRatCoreUp$ face is the common finite scale window read from the same
endpoint ledger, its $\RegSeqRatUp$ face is the regular sequence readback, and
its $\RealUp$ face is the local endpoint seal supplied by the union readback.
There is no second terminal packet with the same displayed rows.

The factorization does not use quotient-real equality, selected limit values,
ambient completeness of $\RealUp$, countable choice, or standard bridge data.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-stream-prefix-probe-union-endpoint-readback}. The synchronized
union window supplies the endpoint $\mathsf{RatHistoryClassifier}$ readback and
the common e-one tail witnesses, all selected from the finite rows of
$\mathcal P,\mathcal Q,\mathcal U$.

Next apply \autoref{thm:streamname-synchronized-window-union-carrier} and
\autoref{thm:streamname-finite-request-section-terminal-coherence}. These two
results identify the $\StreamNameUp$ carrier row with a terminal finite-request
section over the same synchronized window; no endpoint outside $\mathcal U$ is
introduced.

Now apply \autoref{thm:regseqrat-real-terminal-four-face-exactness}. The
RegSeqRat readback and the local Real endpoint seal are thereby read as two
faces of a single terminal packet whose support rows are exactly the displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally apply
\autoref{thm:dyadicratcore-common-scale-window-four-face-pullback-correspondence}.
It supplies the $\DyadicRatCoreUp$ common-scale face and proves that the four
visible faces form one pullback packet. Terminality gives uniqueness of the
packet with those rows, while the construction never introduces quotient-real
equality, selected limits, ambient completeness, countable choice, or standard
bridge data.
\end{proof}

\begin{theorem}[Real stream prefix probe-union terminal four-face support minimality]
\label{thm:real-stream-prefix-probe-union-terminal-four-face-support-minimality}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, finite certified
probe windows $\mathcal P,\mathcal Q$, and their synchronized union
$\mathcal U$, every accepted terminal packet produced by
\autoref{thm:real-stream-prefix-probe-union-terminal-four-face-factorization}
is support-minimal. Deleting or replacing any one of the four faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$, or deleting or replacing
any displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or $\NameCert$ support row,
destroys the accepted probe-union terminal read.

The missing face or support row cannot be supplied by quotient-real equality,
selected limit values, ambient $\RealUp$ completeness, countable choice,
metric-completeness rows, aggregate status rows, or standard bridge data. These
coordinates remain outside the local probe-union packet and do not substitute
for the finite BEDC support rows used by the terminal read.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-stream-prefix-probe-union-terminal-four-face-factorization}.
It identifies the accepted probe-union read with a unique terminal packet whose
visible faces are exactly
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ and whose support is the
displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ row family.

For the finite-window carrier face, apply
\autoref{thm:streamname-terminal-four-face-support-minimality} to the
synchronized StreamName window underlying $\mathcal U$. That result rules out
deletion or replacement of the StreamName face and of the finite probe-history
rows that certify membership in the accepted window.

For the dyadic request and regular tail faces, apply
\autoref{thm:regseqrat-tail-budget-support-minimality}. The common finite scale
window and the RegSeqRat tail-budget rows are read from the same endpoint
ledger, so removing either face, or any of the $\hsame$, $\Cont$, $\Pkg$, or
$\NameCert$ rows it consumes, leaves no accepted regular tail read for the
probe-union endpoint.

Finally apply
\autoref{thm:real-l10-terminal-four-face-support-minimality-pullback} together
with \autoref{thm:real-l10-route-face-deletion-obstruction}. These pull the
Real-side endpoint seal back to the same four-face terminal packet and rule out
substitution by host-real equality, selected limits, completeness coordinates,
choice principles, aggregate status rows, or bridge evidence. The two-axis
roadmap discipline keeps those excluded coordinates separate from the local
BEDC support rows, so none of them can repair a missing face or row.
\end{proof}

\begin{theorem}[Real stream prefix probe-union support-row exchange invariance]
\label{thm:real-stream-prefix-probe-union-support-row-exchange-invariance}
For rational-observation streams $x,y:\mathbb{N}\to\Hist$, let
$\mathcal P$ and $\mathcal Q$ be finite certified $\mathsf{ProbeBundle}$
windows, and let $\mathcal U$ be their synchronized union window. Consider any
two presentations of the terminal packet supplied by
\autoref{thm:real-stream-prefix-probe-union-terminal-four-face-factorization}.
Suppose both presentations preserve the same four visible faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ and the same displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ projections.

Then exchanging the presentation order of those already-displayed support rows
does not produce a second terminal packet. The two presentations determine the
same terminal packet over $\mathcal U$, and for every selected endpoint $j$ they
determine the same finite endpoint readback
$\mathsf{RatHistoryClassifier}(x(j),y(j))$ with the same $\hsame$-transported
common e-one tail witnesses.

This invariance is local to the displayed BEDC support rows. It is not
witnessed by quotient-real equality, selected limit values, ambient
$\RealUp$ completeness, countable choice, aggregate status rows, or bridge
data, and none of those coordinates can distinguish two presentation orders of
the same terminal probe-union packet.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-stream-prefix-probe-union-endpoint-readback}. Both
presentations read each selected endpoint from the same synchronized union
window $\mathcal U$ and the same finite endpoint ledger, so the rational
endpoint row and the common e-one tail witnesses agree by the displayed
$\hsame$ transport.

Next apply
\autoref{thm:real-stream-prefix-probe-union-terminal-four-face-factorization}.
The two presentations expose the same four faces
$\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp$ and the same
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ projections. Terminality
therefore identifies them as one terminal packet over the synchronized union
carrier rather than as two packets distinguished by row order.

Finally apply
\autoref{thm:real-stream-prefix-probe-union-terminal-four-face-support-minimality}.
Support minimality says that the accepted terminal read is carried exactly by
the displayed faces and support rows. Hence quotient-real equality, selected
limits, ambient completeness, countable choice, aggregate status rows, and
bridge data cannot replace one of those rows or separate two orderings of the
same row family. The endpoint readback equality from the first paragraph is
therefore the endpoint readback of the unique terminal packet.
\end{proof}
