\begin{theorem}[Real L10 exit-threshold classifier coherence]
\label{thm:real-l10-exit-threshold-classifier-coherence}
For any finite Phase $\RealUp$ and Completion packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ seal rows, the following two data are equivalent to one displayed four-face record.

First, the packet has public classifier agreement in the sense of the Real L10 four-face classifier pullback and sheaf condition. Second, the same packet satisfies the objectwise exit threshold for the current Phase Real and Completion audit route. The displayed record carries exactly the $\DyadicRatCoreUp$ ledger rows, the $\StreamNameUp$ finite-window rows, the $\RegSeqRatUp$ regularity and common-tail rows, the local $\RealUp$ seal rows, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

The classifier coordinate and the exit-threshold coordinate are read from that same record, but neither coordinate supplies the other. The statement excludes quotient streams, host real equality, selected limits, countable choice, metric-completeness data, $\RealUp$ completeness, aggregate formalstatus rows, and aggregate bridge rows.
\end{theorem}
\begin{proof}
First read the classifier coordinate. Apply \autoref{thm:real-l10-four-face-classifier-pullback} and \autoref{thm:real-l10-four-face-classifier-sheaf-condition}. They identify public classifier agreement with the finite four-face surface over the DyadicRatCore ledger, StreamName finite-window rows, RegSeqRat regularity and common-tail rows, local Real seal rows, and the displayed support rows.

Next read the exit-threshold coordinate. Apply \autoref{thm:real-l10-objectwise-exit-threshold-equivalence}. It says that the current Phase Real and Completion exit threshold is exactly the objectwise threshold over the same four local face records, rather than a route-level aggregate status.

Now combine the two readings. The classifier theorems and the threshold theorem consume the same four concrete faces and the same finite support rows, so their conjunction is equivalent to the single displayed record carrying those rows. In the forward direction, the classifier agreement supplies the classifier face rows and the threshold equivalence supplies the objectwise audit rows on those faces. In the reverse direction, the displayed record feeds the classifier pullback and sheaf condition, and it also feeds the objectwise threshold equivalence.

It remains to show noninterference of the two coordinates. Apply \autoref{thm:real-l10-classifier-status-axis-separation}. Classifier agreement creates no formalstatus, leantarget, bridgestatus, or bridge row, while audit admissibility creates no classifier overlap, finite-window tightness row, pairwise terminal classifier equivalence, or triple common-tail cocycle.

Finally apply \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}. These keep the status and Lean-target data attached to the four displayed faces and rule out an aggregate replacement. Since the cited routes export only the listed finite BEDC rows, no quotient stream, host equality, selected limit, choice principle, metric-completeness datum, $\RealUp$ completeness row, aggregate formalstatus row, or aggregate bridge row is available as an extra coordinate.
\end{proof}

\begin{theorem}[Real L10 classifier-threshold source conservativity]
\label{thm:real-l10-classifier-threshold-source-conservativity}
Let $\mathcal P$ be a finite Real L10 four-face packet satisfying both public classifier agreement and the objectwise exit threshold over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Then the accepted source of $\mathcal P$ is exactly the displayed four-face record over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, local $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Adding the threshold coordinate does not create a fifth source, an aggregate $\formalstatus$ row, an aggregate bridge row, a quotient stream, a selected limit, a metric-completeness datum, a countable-choice row, or a $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
First collapse the hypotheses to one record. By \autoref{thm:real-l10-exit-threshold-classifier-coherence}, public classifier agreement and the objectwise exit threshold are read from the same four-face packet, whose only displayed sources are the DyadicRatCore ledger rows, StreamName finite-window rows, RegSeqRat regularity and common-tail rows, local Real seal rows, and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next identify that record as the accepted source. Apply \autoref{thm:real-l10-four-face-classifier-pullback} to read classifier agreement as the public four-face surface, and apply \autoref{thm:real-l10-objectwise-exit-threshold-equivalence} to read the threshold objectwise on those same faces. The uniqueness comparison is then the source-uniqueness statement of \autoref{thm:dyadicratcore-scale-window-real-exit-source-uniqueness}: the accepted Real exit source is the displayed DyadicRatCore-to-Real four-face route, not an additional carrier.

It remains to separate the source from verification and bridge coordinates. By \autoref{thm:real-l10-classifier-status-axis-separation}, classifier rows do not manufacture $\formalstatus$, leantarget, bridgestatus, or bridge rows, and the audit rows do not manufacture classifier overlap or finite-window tightness data. Thus adjoining the threshold coordinate preserves the four-face source and supplies no aggregate verification or bridge row.

Finally, every excluded object would require a coordinate absent from the four cited readings. Quotient streams and selected limits are not part of the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support; metric completeness, countable choice, and $\RealUp$ completeness are not exported by the objectwise threshold; and an aggregate status or bridge row is ruled out by the axis-separation theorem. Hence the accepted source remains exactly the displayed four-face record.
\end{proof}

\begin{theorem}[Real L10 four-face exit classifier reflection]
\label{thm:real-l10-four-face-exit-classifier-reflection}
For any finite Phase $\RealUp$ and Completion terminal packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows, public classifier agreement on the four-face packet is equivalent to the objectwise Phase Real and Completion exit-threshold read of that same packet precisely when both are reflected from the displayed four-face source record
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp.
$$
The unique reflected source is the finite record carrying exactly the four faces together with the displayed $\BHist$ observations, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance rows, and local $\NameCert$ support rows.

This reflection is only a public classifier and exit-read comparison on the same finite packet. It does not identify quotient streams, host real equality, selected limits, countable-choice selectors, metric-completeness data, $\RealUp$ completeness, aggregate formalstatus rows, aggregate leantarget rows, or aggregate bridge rows.
\end{theorem}
\begin{proof}
First put the classifier coordinate and the threshold coordinate on the same source record. Apply \autoref{thm:real-l10-exit-threshold-classifier-coherence}. It identifies public classifier agreement and the objectwise exit threshold as two readings of one finite four-face packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, the local $\RealUp$ rows, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

For the forward direction, assume public classifier agreement on the terminal four-face packet. The coherence theorem reads the accompanying exit-threshold coordinate from the same displayed record. Then \autoref{thm:real-l10-terminal-pullback-uniqueness} and \autoref{thm:regseqrat-terminal-four-face-source-uniqueness} identify the terminal pullback source and the RegSeqRat source section uniquely, so the reflected source is exactly the stated four-face record.

For the reverse direction, assume the objectwise Phase Real and Completion exit-threshold read is displayed on that record. Use \autoref{thm:real-l10-classifier-threshold-source-conservativity} to keep the accepted source equal to the four-face record, then apply the classifier side of \autoref{thm:real-l10-exit-threshold-classifier-coherence} to recover public classifier agreement on the same packet.

It remains to keep the axes separate. Apply \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}. The closure, verification, Lean-target, and bridge data stay attached to the four displayed faces and cannot be replaced by aggregate rows, while classifier agreement supplies no quotient stream, host equality, selected limit, choice principle, metric-completeness datum, or $\RealUp$ completeness row.
\end{proof}

\begin{theorem}[Real L10 objectwise face-status exit]
\label{thm:real-l10-objectwise-face-status-exit}
For any current Phase $\RealUp$ and Completion exit packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows, the packet satisfies the roadmap exit read exactly when the four local faces each supply their own closurestatus, formalstatus, leantarget, and bridgestatus rows, and the packet carries only the displayed finite support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Equivalently, the exit certificate is the objectwise product of the four local face-status records together with those finite BEDC support rows.

The certificate contains no aggregate $\formalstatus$ row, no aggregate bridge row, no quotient stream, no selected limit, no countable-choice coordinate, no metric-completeness datum, and no $\RealUp$ completeness claim. The local face records remain the exact Phase Real and Completion exit certificate; there is no additional route-level status carrier.
\end{theorem}
\begin{proof}
First read the exit threshold. By \autoref{thm:real-l10-objectwise-exit-threshold-equivalence}, the current Phase Real and Completion threshold is the objectwise threshold on the four displayed faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.

Next recover the local status rows. Apply \autoref{thm:real-l10-current-phase-exit-audit-pullback}. It reads the roadmap audit coordinate from the local closurestatus, formalstatus, leantarget, and bridgestatus rows of those four faces, rather than from a single route credential.

For the forward direction, an accepted roadmap exit read therefore decomposes into exactly the four local face records, and the finite support of the packet is the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. No further support coordinate is introduced by the threshold comparison.

For the reverse direction, suppose the four faces supply those local rows and the packet carries only the displayed BEDC support rows. The audit pullback reads these rows as the current Phase Real and Completion audit record, and the threshold equivalence identifies that record with the roadmap exit read.

It remains to rule out substitute status data. Use \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}. They keep closure, verification, Lean-target, and bridge information attached to the four face chapters, so no aggregate $\formalstatus$, aggregate leantarget, or aggregate bridge row can replace the objectwise certificate.

Finally compare with the StreamName-side certificate of \autoref{thm:streamname-real-completion-objectwise-exit-certificate}. It has the same four-object exit read and the same finite support surface. Thus the Real-side packet is precisely the Phase Real and Completion exit certificate formed by the four local face-status records and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, excluding quotient streams, selected limits, countable choice, metric-completeness data, and $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 exit certificate face minimality]
\label{thm:real-l10-exit-certificate-face-minimality}
Let $\mathcal P$ be an accepted Phase $\RealUp$ and Completion exit certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose $\mathcal P$ satisfies the roadmap exit read by the objectwise four-face certificate of \autoref{thm:real-l10-objectwise-face-status-exit}. Then each of the four face records is indispensable: deleting the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or local $\RealUp$ face record makes the remaining data fail to satisfy the roadmap exit read.

The same minimality holds for the displayed support surface. If any displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, or $\NameCert$ support row used by the four faces is removed, the remaining packet no longer carries an accepted Phase $\RealUp$ and Completion exit certificate under the current Real L10 roadmap read.

This is only a minimality statement for the objectwise exit certificate. It does not introduce quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealL10ExitCertificateFaceMinimality}
\begin{proof}
First identify the certificate whose minimality is being tested. By \autoref{thm:real-l10-objectwise-face-status-exit}, the accepted roadmap exit read is exactly the objectwise product of the four local face-status records together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Next compare the exit read with the current audit route. Apply \autoref{thm:real-l10-current-phase-exit-audit-pullback}. It reads the current Phase Real and Completion audit from those same local face records. Apply \autoref{thm:real-l10-four-face-exit-sufficiency} and \autoref{thm:real-l10-objectwise-exit-threshold-equivalence}. They say that the roadmap exit criterion is satisfied by precisely that four-face objectwise threshold, not by a shortened route.

Now remove one face. If the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or local $\RealUp$ face is absent, the objectwise product required by the face-status theorem is no longer present. The sufficiency theorem therefore has no four-face certificate to consume, and the threshold equivalence cannot read an accepted roadmap exit from the remaining three faces.

Now remove one displayed support row. The face-status theorem lists $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ as the finite support carried by the objectwise certificate. Removing any displayed row breaks the support surface on which the audit pullback and threshold equivalence are evaluated, so the remaining packet does not present the accepted exit certificate.

It remains to rule out replacement data. By \autoref{thm:real-l10-classifier-status-axis-separation}, classifier agreement cannot manufacture formalstatus, leantarget, bridgestatus, or bridge rows, and audit admissibility cannot manufacture classifier rows. By \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}, the status and Lean-target data stay attached to the four displayed faces and cannot be replaced by aggregate rows.

Thus every face record and every displayed support row is indispensable for the current Real L10 roadmap exit read. The cited routes provide no quotient stream, selected limit, countable-choice selector, metric-completeness datum, aggregate formalstatus row, aggregate bridge row, or $\RealUp$ completeness coordinate that could fill the missing position.
\end{proof}

\begin{theorem}[Real L10 exit certificate support no-confusion]
\label{thm:real-l10-exit-certificate-support-no-confusion}
Let $\mathcal P$ and $\mathcal P'$ be accepted Phase $\RealUp$ and Completion exit certificates over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose both certificates expose the same four local face-status records and the same displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then $\mathcal P$ and $\mathcal P'$ determine the same Real L10 exit certificate and the same public finite-section classifier read.

Conversely, equality of Real L10 exit-certificate reads recovers equality of exactly those four local face-status records and the five displayed BEDC support rows. It recovers no quotient stream equality, no selected limit, no countable-choice selector, no metric-completeness datum, no aggregate $\formalstatus$ row, no aggregate bridge row, and no $\RealUp$ completeness claim.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealL10ExitCertificateSupportNoConfusion}
\begin{proof}
First identify the surface on which both certificates are read. By \autoref{thm:real-l10-objectwise-face-status-exit}, an accepted Phase Real and Completion exit certificate is the objectwise product of the four face-status records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows, together with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Since $\mathcal P$ and $\mathcal P'$ expose the same rows, they have the same displayed objectwise exit certificate.

Next rule out hidden alternatives. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. None of the four face records and none of the five support rows can be deleted, replaced, duplicated, or detached while the accepted roadmap exit read is retained. Hence the common displayed surface determines one Real L10 exit-certificate read, so $\mathcal P$ and $\mathcal P'$ cannot separate after the rows listed in the statement have been fixed.

Now transport the same conclusion to the classifier. Apply \autoref{thm:real-l10-exit-threshold-classifier-coherence} to put the exit-threshold read and the public classifier read on one finite four-face record. Then apply \autoref{thm:real-l10-finite-section-classifier-equivalence}. The public finite-section classifier read is exactly the read of the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail classifier rows, the local $\RealUp$ terminal seal row, and the same five support rows. Therefore equal exit-certificate rows give equal public classifier reads.

For the converse direction, assume the two certificate reads are equal. The face-status theorem identifies the only recoverable rows as the four local face-status records and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows; minimality forces equality on each of those rows, because deleting or replacing any one of them would change the accepted certificate read.

Finally separate the certificate vocabulary from verification and bridge data. Use \autoref{thm:real-l10-classifier-status-axis-separation}, \autoref{thm:real-l10-face-status-noncollapse}, and \autoref{thm:real-l10-face-leantarget-noncollapse}. These theorems keep formalstatus, Lean-target, and bridge information local to the four displayed faces and prevent an aggregate route row from being read back out of the certificate. The cited finite rows also contain no quotient stream, selected limit, countable-choice selector, metric-completeness datum, or $\RealUp$ completeness coordinate, so equality of certificate reads recovers none of those data.
\end{proof}

\begin{theorem}[Real L10 finite-section classifier equivalence]
\label{thm:real-l10-finite-section-classifier-equivalence}
Let $\mathcal S$ be a finite Real-and-Completion section over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Public finite-section classifier agreement on $\mathcal S$ is equivalent to the existence of one compatible four-face packet whose rows are exactly the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail classifier rows, the local $\RealUp$ terminal seal row, and the support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

The compatible packet is read objectwise on those four faces. It contains no quotient streams, selected limits, host real equality, countable-choice selectors, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
First put the classifier and threshold readings on one record. Apply \autoref{thm:real-l10-exit-threshold-classifier-coherence}. It identifies the public classifier coordinate and the objectwise exit-threshold coordinate as readings of the same finite four-face packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, local $\RealUp$, and the displayed support rows.

Next identify the reflected source of that record. Apply \autoref{thm:real-l10-four-face-exit-classifier-reflection}. The finite section therefore has the stated public classifier surface exactly when its classifier and exit reads are reflected from the same four-face source
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp.
$$

We now compare the RegSeqRat-facing rows. Apply \autoref{thm:regseqrat-real-terminal-four-face-exactness} to read the local $\RealUp$ terminal seal from the RegSeqRat terminal face, and apply \autoref{thm:regseqrat-common-tail-real-boundary-equivalence} to identify the common-tail classifier rows with the Real boundary rows. This supplies the RegSeqRat regularity, common-tail, and terminal-seal components of the compatible packet.

The StreamName and DyadicRatCore faces are then forced by their finite-section exactness results. Use \autoref{thm:streamname-finite-section-pullback-exactness} to recover the $\StreamNameUp$ finite-window section, and use \autoref{thm:dyadicratcore-common-exponent-window-exactness} to recover the dyadic common scale-window witness. These two faces provide the lower part of the four-face packet and do not introduce any quotient or completeness coordinate.

For the forward direction, public finite-section classifier agreement supplies the four face records just described, and the cited exactness theorems repack them with $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ into the compatible packet. For the reverse direction, a compatible packet carrying exactly those rows feeds the reflected-source theorem and hence yields public finite-section classifier agreement on $\mathcal S$.

Finally apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Each face and each displayed support row is indispensable, so no shortened three-face section or support-free certificate can present the same classifier surface. Since the only rows used are the four local faces and the listed BEDC support rows, the construction has no source for quotient streams, selected limits, host real equality, countable choice, metric-completeness data, aggregate formalstatus, aggregate bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 current-phase exit local threshold]
\label{thm:real-l10-current-phase-exit-local-threshold}
Let $\mathcal E$ be a current Phase $\RealUp$ and Completion exit packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Then $\mathcal E$ satisfies the roadmap exit read exactly when the four objectwise faces $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ each supply their own scoped-closure and audit-clean local threshold rows, and the only support rows carried across the packet are
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

Equivalently, the current Phase Real and Completion exit criterion is the objectwise product of those four local threshold records, reflected through the same finite classifier section, and not a route-level aggregate credential. The packet has no quotient stream, no selected limit, no countable-choice selector, no metric-completeness datum, no aggregate formalstatus row, no aggregate bridge row, and no $\RealUp$ completeness claim.
\end{theorem}
\leanchecked{BEDC.Derived.RealUp.RealL10CurrentPhaseExitLocalThreshold}
\begin{proof}
For the forward direction, assume $\mathcal E$ satisfies the roadmap exit read. By \autoref{thm:real-l10-objectwise-face-status-exit}, the exit read decomposes objectwise into the four face-status records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows, together with only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

The local threshold grade on each face is then read from that same objectwise certificate. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Since each face and each displayed support row is indispensable, the roadmap exit read cannot be witnessed by a shortened section, by an unsupported status row, or by an aggregate credential replacing the four local rows.

For the reverse direction, suppose the four faces each supply their scoped-closure and audit-clean local threshold rows and the packet carries only the displayed BEDC support rows. The objectwise face-status theorem repacks exactly these rows as the current Phase Real and Completion exit certificate, so the roadmap exit read is satisfied.

It remains to identify this certificate with the classifier section used by the roadmap. Apply \autoref{thm:real-l10-four-face-exit-classifier-reflection} to reflect the exit read and public classifier agreement from the same source
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp.
$$
Then apply \autoref{thm:real-l10-finite-section-classifier-equivalence} to read the finite section as exactly the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail classifier rows, the local $\RealUp$ terminal seal row, and the displayed support rows.

Finally combine the minimality and classifier equivalence statements. The four local faces are both necessary and sufficient for the current-phase exit read, and the finite classifier section introduces no extra coordinates. Thus quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, and $\RealUp$ completeness are all absent from the theorem's certificate surface.
\end{proof}

\begin{theorem}[Real L10 finite-request exit cover]
\label{thm:real-l10-finite-request-exit-cover}
Let $\mathcal R$ be a finite Real-and-Completion request section whose visible rows are exactly the $\StreamNameUp$ finite-request section, the $\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the $\RegSeqRatUp$ classifier and regularity rows, the local $\RealUp$ seal row, and the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
Then $\mathcal R$ satisfies the current Phase Real and Completion exit read if and only if those visible rows form the four-face objectwise certificate of \autoref{thm:real-l10-current-phase-exit-local-threshold}.

The cover is finite and objectwise. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First identify the finite request section. Apply \autoref{thm:real-l10-finite-section-classifier-equivalence}. It reads the visible finite section as exactly the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail classifier rows, the local $\RealUp$ terminal seal row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

For the forward direction, assume $\mathcal R$ satisfies the current Phase Real and Completion exit read. By \autoref{thm:real-l10-current-phase-exit-local-threshold}, that exit read is precisely the objectwise product of the four local threshold records on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, carried by the same displayed support rows. The finite-section equivalence identifies these rows with the visible request section, so the section forms the required four-face certificate.

For the reverse direction, suppose the visible rows of $\mathcal R$ form that four-face objectwise certificate. The current-phase local-threshold theorem consumes exactly those four face records and the displayed support rows, so the roadmap exit read is satisfied.

It remains to rule out shortened or enlarged covers. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Each of the four face records and each displayed support row is indispensable for the current Real L10 exit certificate, so a missing face, a missing support row, or an added aggregate credential cannot present the same exit read.

Therefore the finite request section is a cover of the current exit certificate exactly in the stated objectwise sense. The cited theorems provide no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 exit-certificate dependency factorization]
\label{thm:real-l10-exit-certificate-dependency-factorization}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion exit packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Then $\mathcal E$ satisfies the current-phase exit local threshold if and only if its accepted exit certificate factors through exactly the ordered dependency surface
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
together with the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$

In the forward direction, an accepted exit certificate decomposes into the four face records: the finite-tail $\DyadicRatCoreUp$ exit certificate, the $\StreamNameUp$ ordered finite-window gate, the $\RegSeqRatUp$ finite-section classifier record, and the local $\RealUp$ seal-facing threshold record, all carried by those same support rows. In the reverse direction, those four compatible face records repack to the accepted current-phase exit local threshold certificate for $\mathcal E$.

This factorization excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness. It is only a dependency certificate for the finite Phase Real and Completion exit surface.
\end{theorem}
\begin{proof}
For the forward direction, assume $\mathcal E$ satisfies the current-phase exit local threshold. Apply \autoref{thm:real-l10-current-phase-exit-local-threshold}. The threshold read is the objectwise product of the four local threshold records on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, with no support beyond $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Now identify the four components of that product. The DyadicRatCore component is the finite-tail exit-certificate surface of \autoref{thm:dyadicratcore-finite-tail-exit-certificate-equivalence}. The StreamName component is constrained by \autoref{thm:streamname-l10-four-face-ordered-exit-gate}, so the consumer-facing read keeps the displayed StreamName window before the dyadic ledger and then the RegSeqRat and Real faces.

The middle and terminal components are read from the finite section. Apply \autoref{thm:real-l10-finite-section-classifier-equivalence} to identify the $\RegSeqRatUp$ classifier and regularity rows together with the local $\RealUp$ terminal seal row. Then apply \autoref{thm:real-l10-exit-certificate-face-minimality}: none of these four faces, and none of the displayed support rows, can be deleted or replaced by an aggregate credential.

For the reverse direction, suppose the packet displays exactly those four compatible face records over the ordered surface and the displayed support rows. The finite-section classifier equivalence repacks the StreamName, RegSeqRat, dyadic scale-window, and local Real rows as one finite request section, while the StreamName ordered exit gate supplies the consumer-facing order.

The DyadicRatCore finite-tail exit-certificate equivalence supplies the first visible face of the objectwise certificate. Combining that dyadic face with the StreamName, RegSeqRat, and Real rows gives the four-face certificate consumed by \autoref{thm:real-l10-finite-request-exit-cover}. Hence the visible section satisfies the current Phase Real and Completion exit read.

Finally apply \autoref{thm:real-l10-current-phase-exit-local-threshold} again to identify that exit read with the current-phase local threshold for $\mathcal E$. Since every cited theorem works only with the four displayed faces and the rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, there is no coordinate from which to form quotient streams, selected limits, countable-choice data, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 construction-consumer order square]
\label{thm:real-l10-construction-consumer-order-square}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose $\mathcal E$ satisfies the current-phase exit local threshold. Then the construction-source projection
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp
$$
and the consumer-readback projection
$$
\StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \RealUp
$$
are the two visible edge readings of one commuting square of the same displayed four-face exit certificate.

The top edge is the Real-side source reflection, the left edge is the StreamName finite-window readback, the right edge is the RegSeqRat-to-Real seal read, and the bottom edge is the shared objectwise certificate. Commutativity means that reading the packet by the construction source and then consuming it through the StreamName-facing gate yields the same four local face records and the same displayed support rows as first reading the consumer gate and then projecting to the Real-side source. The square supplies no quotient stream equality, selected limit, countable-choice row, metric-completeness datum, aggregate formalstatus row, aggregate bridge row, standard bridge row, or $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
First read the Real-side source. By \autoref{thm:real-l10-four-face-exit-classifier-reflection}, the classifier and exit-threshold coordinates of $\mathcal E$ are reflected from the displayed source
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp.
$$
By \autoref{thm:real-l10-current-phase-exit-local-threshold}, this source carries exactly the four objectwise local threshold records and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Next read the consumer-facing order. Apply \autoref{thm:streamname-l10-four-face-ordered-exit-gate}. The same accepted Phase Real and Completion seal-facing read is consumed along
$$
\StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \RealUp,
$$
where the StreamName finite window is read before the dyadic ledger, the RegSeqRat readback is anchored to those rows, and the RealUp seal is read last.

The two readings now have the same certificate target. Use \autoref{thm:real-l10-exit-certificate-face-minimality}: each of the four face records and each displayed support row is indispensable for the current Real L10 exit certificate. Therefore neither route can replace, delete, or duplicate a face while still presenting the accepted exit read.

Finally compare the edge maps. The Real-side reflection gives the construction-source edge, the StreamName ordered gate gives the consumer-readback edge, and the local-threshold theorem identifies both with the same objectwise certificate. Since face minimality leaves only those four faces and those support rows, the square commutes as a comparison of projections of one displayed certificate, not as a second completion route.

All excluded data remain absent. The cited theorems export only the finite face rows and the displayed support rows, so the square has no source for quotient stream equality, selected limits, countable choice, metric completeness, aggregate formalstatus, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 finite-request exit cocycle]
\label{thm:real-l10-finite-request-exit-cocycle}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion request packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose $\mathcal E$ satisfies the current-phase exit local threshold. Then the DyadicRatCore finite-tail exit certificate, the StreamName finite-request section pullback exactness, the RegSeqRat four-face exit-threshold equivalence, and the Real finite-request exit cover form one associative cocycle on the same four-face source.

Equivalently, the construction-source-then-consumer-readback composite and the RegSeqRat-threshold-then-Real-exit-cover composite recover exactly the same four face records and the same support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert.
$$
The cocycle is only a finite packet identity among these four visible readings. It supplies no quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the dyadic face. By \autoref{thm:dyadicratcore-finite-tail-exit-certificate-equivalence}, the visible $\DyadicRatCoreUp$ input to $\mathcal E$ is exactly the finite-tail exit certificate carried by the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. This gives the first edge of the finite four-face source.

Next attach the request section. Apply \autoref{thm:streamname-finite-request-section-pullback-exactness}. The StreamName finite request section is pulled back over that same dyadic face, so the consumer readback does not introduce a second support surface or a second certificate target.

Now read the terminal threshold. Apply \autoref{thm:regseqrat-four-face-exit-threshold-equivalence}. The RegSeqRat threshold is the terminal four-face reading of the dyadic and StreamName data together with the local $\RealUp$ seal row, and it keeps the same five support rows.

The Real exit cover is the last face. By \autoref{thm:real-l10-finite-request-exit-cover}, the finite request section covers exactly the Real exit certificate visible from the same four faces. Thus the RegSeqRat-threshold-then-Real-exit-cover route returns the same records as the preceding dyadic and StreamName pullback route.

It remains to compare the two edge orders. Use \autoref{thm:real-l10-construction-consumer-order-square}: the construction-source projection and the consumer-readback projection are two readings of one commuting square of the displayed four-face exit certificate. Therefore composing through the construction edge before the consumer edge, or through the RegSeqRat terminal threshold before the Real cover, is associative as a cocycle on the same finite packet.

All exclusions are inherited from the cited faces. None of them exports quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, or $\RealUp$ completeness, so the cocycle cannot add such data.
\end{proof}

\begin{theorem}[Real L10 support-row reindexing invariance]
\label{thm:real-l10-face-order-permutation-invariance}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion packet satisfying the current-phase exit local threshold of \autoref{thm:real-l10-current-phase-exit-local-threshold}. Let $O$ and $O'$ be accepted support-row-preserving reindexings or projections of the ordered terminal route fixed by \autoref{thm:streamname-l10-four-face-ordered-exit-gate}:
$$
\StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \RealUp .
$$
Assume that both readings preserve the same displayed face rows, the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and the same local $\RealUp$ seal row. Assume also that neither reading detaches the $\DyadicRatCoreUp$ ledger from the $\StreamNameUp$ finite window, reads the $\RegSeqRatUp$ row before the dyadic predecessor face, or reads the $\RealUp$ seal before the required predecessor faces. Then $O$ and $O'$ determine the same objectwise Phase $\RealUp$ and Completion exit certificate.

The invariant certificate is only the finite four-face objectwise product over the ordered terminal route and its displayed support rows. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First fix the public route. Apply \autoref{thm:streamname-l10-four-face-ordered-exit-gate}. An accepted seal-facing read satisfies the public L10 exit gate only along
$$
\StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \RealUp,
$$
with the finite StreamName window before the dyadic ledger, the RegSeqRat readback after the anchored ledger, and the RealUp seal last. Thus $O$ and $O'$ are not arbitrary face permutations; they are support-row-preserving views of that same ordered terminal route.

Next identify the certificate carried by that route. By \autoref{thm:real-l10-current-phase-exit-local-threshold}, the current Phase Real and Completion exit criterion is the objectwise product of the four local threshold records for $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, together with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Use minimality to control the allowed reindexings and projections. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Since every one of the four face records and every displayed support row is indispensable, an accepted support-row-preserving view cannot delete, duplicate, detach, or replace a face or support row while still presenting the same current Real L10 exit certificate.

Now compare $O$ and $O'$ as finite classifier sections of the same terminal packet. By \autoref{thm:real-l10-finite-section-classifier-equivalence}, every accepted finite-section read with these four faces and these support rows is a compatible four-face packet over the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail rows, and the local $\RealUp$ terminal seal row.

Thus both $O$ and $O'$ are projections of the same compatible finite packet over the ordered route. The construction-consumer square of \autoref{thm:real-l10-construction-consumer-order-square} is one visible comparison inside this finite certificate, and the present hypotheses restrict the comparison to order-preserving support reindexings or projections of the same four-face certificate.

The conclusion is therefore support-row reindexing invariance of the displayed objectwise exit certificate, not a second route to completion and not a permission to permute the public L10 construction faces. The cited theorems provide no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness, so these data remain outside the invariant certificate.
\end{proof}

\begin{theorem}[Real L10 face-local formal upgrade invariance]
\label{thm:real-l10-face-local-formal-upgrade-invariance}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows satisfying the current-phase exit local threshold of \autoref{thm:real-l10-current-phase-exit-local-threshold}. Let $F$ be one of the four displayed faces. Form $\mathcal E_F^+$ by replacing only the local formal-status row attached to $F$ by a strictly stronger local formal-status row, or by replacing only the leantarget row or bridgestatus row attached to $F$ by a replacement row attached to the same face whose recorded target or bridge status refines the same local face without changing the other three face records.

Assume that the displayed support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ are unchanged. Then $\mathcal E_F^+$ determines the same four-face Phase $\RealUp$ and Completion exit certificate as $\mathcal E$. Conversely, any packet with the same four-face exit certificate and with all non-$F$ face records and displayed support rows fixed differs from $\mathcal E$ only by a face-local formal-status strengthening on $F$, or by a face-local leantarget or bridgestatus refinement attached to $F$ that preserves the same displayed certificate surface.

This invariance is purely face-local. It does not introduce route-level formalstatus, aggregate leantarget rows, aggregate bridge rows, selected limits, quotient streams, metric-completeness data, $\RealUp$ completeness, or any replacement for the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.
\end{theorem}
\begin{proof}
First identify the certificate whose stability is being tested. By \autoref{thm:real-l10-objectwise-face-status-exit}, the accepted Phase $\RealUp$ and Completion exit certificate is the objectwise product of the four local face-status records together with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

For the forward direction, first consider a strictly stronger local formal-status row attached to $F$. The other three face records and all displayed support rows are unchanged, so the objectwise product still has the same four faces and the same finite BEDC support surface. By \autoref{thm:real-l10-face-status-noncollapse}, the stronger formal-status data remains attached to $F$ and cannot become a route-level aggregate row.

The leantarget and bridgestatus alternatives are same-face refinements rather than entries in a shared strengthening order. Their recorded target or bridge status remains attached to $F$, refines that local face, and preserves the other three face records together with the displayed support rows. By \autoref{thm:real-l10-face-leantarget-noncollapse}, the Lean-target refinement cannot become an aggregate route row, and the objectwise face-status certificate keeps bridge-status information on the displayed local face surface.

Now use support-row invariance. Apply \autoref{thm:real-l10-face-order-permutation-invariance}. Since the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are fixed and no face is detached or reordered outside the accepted terminal route, the finite BEDC packet presents the same objectwise exit certificate after the local strengthening.

For the converse direction, suppose a packet presents the same four-face exit certificate while the three non-$F$ face records and all displayed support rows are fixed. By \autoref{thm:real-l10-exit-certificate-face-minimality}, none of the four faces and none of the displayed support rows can be deleted, aggregated, duplicated, or replaced while the same current Real L10 exit certificate is retained.

It remains only to locate the possible difference. The non-$F$ records are fixed by hypothesis, and minimality fixes the displayed support surface. The noncollapse theorems keep formalstatus and Lean-target rows attached to their source face, while the objectwise face-status theorem keeps bridge-status information local to the four displayed faces. Hence any remaining difference is either a stronger local formal-status row on $F$, or a same-face leantarget or bridgestatus refinement on $F$ that preserves the displayed certificate surface.

All excluded data remain absent. The cited results use only the four face records and the displayed support rows; they provide no route-level formalstatus, aggregate bridge coordinate, selected limit, quotient stream, metric-completeness datum, or $\RealUp$ completeness row. Thus the certificate is invariant precisely under the stated face-local formal strengthening and same-face leantarget or bridgestatus refinement.
\end{proof}

\begin{theorem}[Real L10 face formal upgrade chain invariance]
\label{thm:real-l10-face-formal-upgrade-chain-invariance}
Let
$$
\mathcal E_0,\mathcal E_1,\ldots,\mathcal E_n
$$
be a finite sequence of Phase $\RealUp$ and Completion packets over the four displayed faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp .
$$
Assume $\mathcal E_0$ satisfies the current-phase exit local threshold of \autoref{thm:real-l10-current-phase-exit-local-threshold}. For each adjacent step $\mathcal E_i\leadsto\mathcal E_{i+1}$, assume exactly one face is changed, the changed row is a same-face formalstatus strengthening, leantarget refinement, or bridgestatus refinement, and all other face records are fixed. Assume also that every step preserves the displayed support rows
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
Then every intermediate packet $\mathcal E_i$ determines the same objectwise Phase $\RealUp$ and Completion exit certificate read by \autoref{thm:real-l10-current-phase-exit-local-threshold}.

The invariant certificate is only the finite four-face exit certificate. The sequence supplies no aggregate formalstatus row, aggregate leantarget row, aggregate bridge row, quotient stream, selected limit, countable-choice selector, metric-completeness datum, standard bridge row, or $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Induct on the finite sequence. The base case is the one-packet sequence, where the exit certificate is the certificate of $\mathcal E_0$ read by \autoref{thm:real-l10-current-phase-exit-local-threshold}.

For the induction step, suppose $\mathcal E_i$ has the same objectwise exit certificate as $\mathcal E_0$. The adjacent move $\mathcal E_i\leadsto\mathcal E_{i+1}$ changes only one of the four displayed faces, and the change is either a stronger local formalstatus row, a same-face leantarget refinement, or a same-face bridgestatus refinement. The rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ remain fixed.

Apply \autoref{thm:real-l10-face-local-formal-upgrade-invariance} to this adjacent move. It identifies the exit certificate of $\mathcal E_{i+1}$ with the exit certificate of $\mathcal E_i$, because the refinement remains attached to its source face and does not alter the other three face records or the displayed support surface.

Finally use transitivity of the certificate comparison supplied by the induction hypothesis. The noncollapse theorems \autoref{thm:real-l10-face-status-noncollapse} and \autoref{thm:real-l10-face-leantarget-noncollapse}, together with the minimality theorem \autoref{thm:real-l10-exit-certificate-face-minimality}, exclude aggregate formalstatus rows, aggregate bridge rows, quotient streams, selected limits, metric-completeness data, and $\RealUp$ completeness at every step. Hence each intermediate packet reads the same finite four-face Phase Real and Completion exit certificate.
\end{proof}

\begin{theorem}[Real L10 exit-threshold face-local correspondence]
\label{thm:real-l10-exit-threshold-face-local-correspondence}
Let $\mathcal E$ be a finite Phase $\RealUp$ and Completion packet over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Then $\mathcal E$ satisfies the current-phase exit local threshold of \autoref{thm:real-l10-current-phase-exit-local-threshold} if and only if it exhibits four compatible local face records over the same displayed support rows:
\begin{enumerate}
\item the $\DyadicRatCoreUp$ finite-tail certificate,
\item the $\StreamNameUp$ ordered finite-window gate,
\item the $\RegSeqRatUp$ finite-section classifier record,
\item the local $\RealUp$ seal-facing threshold record.
\end{enumerate}
Compatibility means that all four records are read over the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows, and that no face record is detached from the ordered terminal route.

This correspondence is exactly local-record correspondence for the four displayed faces, not an aggregate audit credential. It recovers no quotient stream, selected limit, countable-choice selector, metric-completeness datum, aggregate formalstatus row, aggregate bridge row, standard bridge row, or $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
For the forward direction, read the threshold by \autoref{thm:real-l10-current-phase-exit-local-threshold}. The accepted exit read is the objectwise product of the four local threshold records on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, together with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Now factor that read through the displayed route. Apply \autoref{thm:real-l10-exit-certificate-dependency-factorization}. The dyadic finite-tail certificate, the ordered StreamName finite-window gate, the RegSeqRat finite-section classifier record, and the local Real seal-facing threshold record are the four ordered faces of the same exit certificate rather than independent summaries.

Minimality fixes the vocabulary of the correspondence. By \autoref{thm:real-l10-exit-certificate-face-minimality}, none of the four face records and none of the displayed support rows can be deleted, duplicated, detached, or replaced while the same current Real L10 exit certificate is retained. Thus the forward read produces exactly the listed local records over the common support surface.

For the reverse direction, assume the four compatible local records are exhibited over the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Use \autoref{thm:real-l10-exit-certificate-refinement-functoriality} to compare this displayed four-face section with the finite packet $\mathcal E$: the support-row-preserving comparison recovers the same objectwise certificate read.

Finally apply \autoref{thm:real-l10-current-phase-exit-local-threshold} again. Since the recovered objectwise certificate is precisely the product of the dyadic finite-tail certificate, the ordered StreamName finite-window gate, the RegSeqRat finite-section classifier record, and the local Real seal-facing threshold record, the packet satisfies the current-phase exit local threshold.

Face-local formal changes do not alter the equivalence. By \autoref{thm:real-l10-face-local-formal-upgrade-invariance}, any strengthening of a local status, leantarget, or bridge-status row remains attached to its source face and cannot become a route-level aggregate credential. Consequently the correspondence has no coordinate for quotient streams, selected limits, countable-choice selectors, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 exit certificate refinement functoriality]
\label{thm:real-l10-exit-certificate-refinement-functoriality}
Let $\mathcal E$ and $\mathcal E'$ be finite Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose $\rho : \mathcal E \to \mathcal E'$ is a certified finite refinement whose visible action preserves each displayed face row and preserves the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Then $\mathcal E$ and $\mathcal E'$ determine the same objectwise Phase Real and Completion exit certificate read by \autoref{thm:real-l10-current-phase-exit-local-threshold}.

Conversely, if $\mathcal E$ and $\mathcal E'$ determine the same objectwise Phase Real and Completion exit certificate, then the equality recovers exactly a certified finite refinement between their displayed four-face sections that preserves the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ rows and preserves the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

This refinement law is confined to the displayed finite certificate surface. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First read both packets through the current exit criterion. By \autoref{thm:real-l10-current-phase-exit-local-threshold}, each accepted packet is read as the objectwise product of the four local threshold records on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, together with exactly the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

For the forward direction, apply the certified finite refinement $\rho$. Its visible action preserves every one of the four face rows and every displayed support row, so the finite-section read of $\mathcal E'$ has the same rows as the finite-section read of $\mathcal E$. By \autoref{thm:real-l10-finite-section-classifier-equivalence}, the two finite sections therefore present the same compatible four-face classifier packet.

Now control possible reorderings or local status changes introduced by the refinement. Apply \autoref{thm:real-l10-face-order-permutation-invariance} to identify support-row-preserving views of the terminal route with the same objectwise exit certificate. Apply \autoref{thm:real-l10-face-local-formal-upgrade-invariance} to keep any face-local formal strengthening attached to its source face rather than to an aggregate route row.

For the converse direction, assume that $\mathcal E$ and $\mathcal E'$ determine the same objectwise exit certificate. By \autoref{thm:real-l10-exit-certificate-face-minimality}, none of the four face rows and none of the displayed support rows can be deleted, duplicated, detached, or replaced while the same certificate is retained.

The finite-section classifier equivalence then reconstructs the only possible comparison between the two visible sections: it is the support-row-preserving finite refinement carrying the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ rows to the corresponding rows and carrying the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows to themselves. Minimality makes this refinement exact, because there is no unused face coordinate or hidden support coordinate on which a different refinement could act.

All exclusions are inherited from the same cited certificate surface. The argument uses only finite face rows, finite classifier sections, support-row-preserving route views, and face-local formal strengthening; it has no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 exit certificate refinement composition]
\label{thm:real-l10-exit-certificate-refinement-composition}
Let $\mathcal E_0$, $\mathcal E_1$, and $\mathcal E_2$ be finite Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose
$$
\mathcal E_0 \xrightarrow{\rho_{01}} \mathcal E_1 \xrightarrow{\rho_{12}} \mathcal E_2
$$
is a pair of certified finite refinements. Assume that each leg preserves the four displayed face rows $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$, and preserves the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Then the composite refinement $\rho_{12}\circ\rho_{01}$ preserves the same displayed face and support rows, and $\mathcal E_0$ and $\mathcal E_2$ determine the same objectwise Phase Real and Completion exit certificate read by \autoref{thm:real-l10-current-phase-exit-local-threshold}.

Equivalently, a finite chain of two certified refinements cannot create any additional exit-coordinate between the endpoints. The endpoint certificate is still exactly the compatible four-face packet on $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ face, together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

This composition law is confined to finite support-row-preserving refinements. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First apply \autoref{thm:real-l10-exit-certificate-refinement-functoriality} to the first leg $\rho_{01}$. The hypotheses say that the visible action of $\rho_{01}$ preserves each of the four displayed face rows and every displayed support row, so $\mathcal E_0$ and $\mathcal E_1$ determine the same objectwise exit certificate.

Apply the same theorem to the second leg $\rho_{12}$. The second visible action preserves the same four face rows and the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so $\mathcal E_1$ and $\mathcal E_2$ determine the same objectwise exit certificate.

Now identify the intermediate certificate. By \autoref{thm:real-l10-finite-section-classifier-equivalence}, the finite sections read from $\mathcal E_0$, $\mathcal E_1$, and $\mathcal E_2$ are compatible four-face packets over the same displayed terminal surface: the dyadic common scale-window witness, the finite $\StreamNameUp$ window, the $\RegSeqRatUp$ regularity and common-tail rows, and the local $\RealUp$ seal row. Hence the equality through $\mathcal E_1$ is equality of the same finite classifier packet, not merely agreement of unrelated summaries.

It remains to read the composite. Since both legs preserve every displayed face row and every displayed support row, their composite also sends each $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ row to the corresponding endpoint row and sends the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows to the corresponding endpoint rows. Transitivity of the two objectwise certificate identifications gives the endpoint certificate equality between $\mathcal E_0$ and $\mathcal E_2$.

Finally apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Minimality rules out any hidden coordinate on which the composite could act while preserving the current Real L10 exit certificate: no quotient stream, selected limit, metric-completeness datum, aggregate formalstatus row, aggregate bridge row, standard bridge row, or $\RealUp$ completeness row is part of the finite certificate surface. Thus the two-leg chain composes only as a support-row-preserving refinement of the same displayed objectwise exit certificate.
\end{proof}

\begin{theorem}[Real L10 exit certificate refinement zigzag invariance]
\label{thm:real-l10-exit-certificate-refinement-zigzag}
Let $\mathcal E_0,\ldots,\mathcal E_n$ be a finite zigzag of Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Assume that every adjacent step is a certified support-row-preserving finite refinement in one direction or the other, preserving the four displayed face rows and preserving the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Then all packets $\mathcal E_i$ determine the same objectwise Phase Real and Completion exit certificate read by \autoref{thm:real-l10-current-phase-exit-local-threshold}.

Conversely, let $\mathcal E_0,\ldots,\mathcal E_n$ be a finite family of Phase $\RealUp$ and Completion packets over the same four displayed faces. If all packets determine one common objectwise Phase Real and Completion exit certificate, then the family admits a common support-row-preserving refinement zigzag through the displayed four-face sections. Each adjacent comparison preserves the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ rows and preserves the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

This finite-zigzag invariant is confined to the displayed four-face certificate surface. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
For the forward direction, induct on the length of the finite zigzag. The empty zigzag and the one-packet zigzag read a single packet through \autoref{thm:real-l10-current-phase-exit-local-threshold}, so there is no comparison to transport.

For the induction step, remove the last adjacent comparison. The induction hypothesis identifies the objectwise exit certificate of every earlier packet with the certificate of the penultimate packet. The final adjacent comparison is a certified support-row-preserving finite refinement in one direction or the other, so \autoref{thm:real-l10-exit-certificate-refinement-functoriality} identifies the penultimate and final certificate readings. Transitivity of equality of the objectwise certificate readings composes these identifications and gives one certificate for the whole zigzag.

For the converse direction, assume the finite family has one common objectwise exit certificate. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Since the four displayed face rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are indispensable, no member of the family can realize that common certificate by deleting, duplicating, detaching, or replacing one of those rows.

Next apply \autoref{thm:real-l10-finite-section-classifier-equivalence}. Each packet therefore has a displayed four-face section over the same dyadic common scale-window witness, the same finite $\StreamNameUp$ window, the same $\RegSeqRatUp$ regularity and common-tail rows, and the same local $\RealUp$ terminal seal row. The only possible adjacent comparisons between consecutive displayed sections are the support-row-preserving certified finite refinements recovered by \autoref{thm:real-l10-exit-certificate-refinement-functoriality}.

Ordering the finite family by its displayed indices and inserting these recovered adjacent comparisons gives the required common refinement zigzag. Its support surface is exactly the four-face section just described, so the construction has no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 exit refinement common envelope]
\label{thm:real-l10-exit-refinement-common-envelope}
Let
$$
\mathcal E_0,\ldots,\mathcal E_n
$$
be a finite zigzag of Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Assume that every adjacent step is a certified support-row-preserving finite refinement in one direction or the other, preserving the four displayed face rows and preserving the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Then there is a single finite envelope record carrying exactly the four face rows
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp,
$$
and exactly the displayed support rows
$$
\BHist,\qquad \hsame,\qquad \Cont,\qquad \Pkg,\qquad \NameCert,
$$
through which every packet's objectwise Phase Real and Completion exit certificate factors.

The envelope is the common finite four-face certificate surface, not an ambient completion object. It has no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First identify the common certificate. Apply \autoref{thm:real-l10-exit-certificate-refinement-zigzag} to the finite zigzag. The adjacent support-row-preserving refinements give one objectwise Phase Real and Completion exit certificate shared by every $\mathcal E_i$.

Next decompose that shared certificate into its local faces. By \autoref{thm:real-l10-exit-threshold-face-local-correspondence}, the common objectwise certificate is represented by the dyadic finite-tail certificate, the ordered $\StreamNameUp$ finite-window gate, the $\RegSeqRatUp$ finite-section classifier record, and the local $\RealUp$ seal-facing threshold record, all read over the same displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Now order the four records through the dependency surface. Apply \autoref{thm:real-l10-exit-certificate-dependency-factorization}. The face records factor through the dyadic source, the stream-name window, the regular-sequence common-tail classifier, and the local Real terminal seal in that order, so they form one finite envelope record rather than four unrelated local summaries.

It remains to show that the envelope has exactly the displayed vocabulary. The current-phase threshold theorem \autoref{thm:real-l10-current-phase-exit-local-threshold} supplies only the four displayed face rows and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The minimality theorem \autoref{thm:real-l10-exit-certificate-face-minimality} then rules out deleting, duplicating, detaching, or replacing any of those rows while preserving the same exit certificate.

The same minimality argument excludes every forbidden coordinate. Quotient streams, selected limits, countable-choice selectors, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness are not part of the finite four-face certificate surface. Hence the common objectwise certificate of each $\mathcal E_i$ factors through the single finite envelope and through no larger hidden carrier.
\end{proof}

\begin{theorem}[Real L10 finite-request subfamily exit stability]
\label{thm:real-l10-finite-request-subfamily-exit-stability}
Let $\{\mathcal E_i\}_{i \in I}$ be a finite family of Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose the family has one common objectwise Phase Real and Completion exit certificate, and suppose that every finite request subfamily $J \subseteq I$ preserves the four displayed face rows
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp,
$$
together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Then each finite request subfamily $J$ determines the same objectwise Phase Real and Completion exit certificate as the ambient family. Conversely, any subfamily that determines that same certificate is obtained by restricting the displayed four-face sections and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows to the retained requests.

This stability is only a finite-request restriction statement. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, and $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First read the ambient family through the common certificate. Apply \autoref{thm:real-l10-exit-certificate-refinement-zigzag}. Since all members determine one objectwise Phase Real and Completion exit certificate, the family admits a common support-row-preserving refinement zigzag through the displayed four-face sections.

Now restrict to a finite request subfamily $J \subseteq I$. The RegSeqRat-side restriction source is \autoref{thm:regseqrat-common-tail-terminal-section-restriction-exactness}: finite subfamily restriction of the common-tail terminal section cover keeps exactly the retained $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and adds no hidden completion or choice coordinate.

Identify the restricted Real L10 section. By \autoref{thm:real-l10-finite-section-classifier-equivalence}, the retained finite request section is still the compatible four-face packet over the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail rows, and the local $\RealUp$ terminal seal row, together with the displayed support rows.

Minimality prevents the restriction from changing the certificate vocabulary. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. None of the four face rows and none of the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows can be deleted, replaced, duplicated, or detached while retaining the same current Real L10 exit certificate.

Thus the restricted subfamily has the same objectwise certificate as the ambient family. For the converse direction, suppose a subfamily has that same certificate. The same minimality theorem forces its visible rows to be exactly retained rows from the ambient four-face section and displayed support surface, and the finite-section classifier equivalence identifies the retained rows as the restricted finite section. Hence the subfamily is precisely the restriction of the four displayed face sections and support rows to its retained requests.

The exclusion clauses follow from the same row accounting. The cited Real L10 and RegSeqRat theorems expose only finite four-face sections and the displayed support rows; they provide no coordinate for quotient streams, selected limits, countable choice, metric-completeness data, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Real L10 finite-request intersection exit exactness]
\label{thm:real-l10-finite-request-intersection-exit-exactness}
Let $\{\mathcal E_i\}_{i \in I}$ be a finite family of Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose the ambient family has one common objectwise Phase Real and Completion exit certificate, and let $J,K \subseteq I$ be finite request subfamilies whose restrictions preserve the four displayed face rows together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Then the finite intersection $J \cap K$ determines the same objectwise exit certificate as the two restricted request subfamilies exactly when the retained $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, local $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows agree on $J \cap K$. In that case the intersection certificate is the objectwise restriction of the common Phase Real and Completion certificate to the retained requests, and no further exit coordinate is present on the overlap.

This exactness is confined to finite overlaps of request subfamilies inside the displayed Real L10 four-face surface. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate status rows, aggregate bridge rows, standard bridge rows, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First restrict each request subfamily. By \autoref{thm:real-l10-finite-request-subfamily-exit-stability}, the $J$-restriction and the $K$-restriction both determine the same objectwise Phase Real and Completion exit certificate as the ambient family, and each restriction keeps exactly the displayed four-face rows and the displayed support rows on its retained requests.

Now pass to the overlap. Apply \autoref{thm:regseqrat-common-tail-terminal-section-intersection-exactness} to the RegSeqRat common-tail terminal sections underlying the two restrictions. The theorem identifies the retained $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows on the finite meet $J \cap K$, and it supplies no quotient stream, selected limit, countable-choice row, or hidden completion datum.

Use \autoref{thm:real-l10-finite-section-classifier-equivalence} to read that finite meet as a Real L10 section. The retained overlap is therefore the same compatible four-face packet over the dyadic common scale-window witness, the finite $\StreamNameUp$ window, the $\RegSeqRatUp$ regularity and common-tail rows, and the local $\RealUp$ terminal seal row, together with the same displayed support rows.

It remains to prove exactness rather than mere compatibility. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Since every displayed face row and every displayed support row is indispensable for the current Real L10 exit certificate, agreement of those retained rows on $J \cap K$ is sufficient for the same objectwise exit read, and any disagreement among them prevents the two restricted presentations from determining one overlap certificate.

Thus $J \cap K$ determines the same objectwise exit certificate precisely in the stated rowwise case. The cited restriction, intersection, classifier, and minimality results account for all certificate coordinates, so aggregate status rows, aggregate bridge rows, standard bridge rows, metric-completeness data, and ambient $\RealUp$ completeness cannot be inserted on the overlap.
\end{proof}

\begin{theorem}[Real L10 finite-request union exit exactness]
\label{thm:real-l10-finite-request-union-exit-exactness}
Let $\{\mathcal E_i\}_{i \in I}$ be a finite family of Phase $\RealUp$ and Completion packets over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ rows. Suppose the ambient family has one common objectwise Phase Real and Completion exit certificate, and let $J,K \subseteq I$ be finite request subfamilies whose restrictions preserve the four displayed face rows together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows. Suppose also that the retained rows on $J$, on $K$, and on $J \cap K$ agree on the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, local $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Then the finite union $J \cup K$ determines the same objectwise Phase Real and Completion exit certificate as the two restricted request subfamilies exactly when the displayed union contains no rows beyond the four listed faces and the displayed support rows. In that case the union certificate is the objectwise restriction of the common Phase Real and Completion certificate to $J \cup K$.

This exactness is confined to finite unions of request subfamilies inside the displayed Real L10 four-face surface. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate status rows, aggregate bridge rows, standard bridge rows, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First restrict each side. By \autoref{thm:real-l10-finite-request-subfamily-exit-stability}, the $J$-restriction and the $K$-restriction both determine the same objectwise Phase Real and Completion exit certificate as the ambient family, and each restriction keeps exactly the displayed four-face rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

The overlap hypothesis is the compatibility datum for gluing. Apply \autoref{thm:real-l10-finite-request-intersection-exit-exactness} to $J \cap K$. The common rows on the meet identify the two restricted presentations on their shared retained requests, so the union can be read as one finite request surface rather than as two unrelated certificates.

Now assemble the four-face union surface. Use \autoref{thm:streamname-finite-window-union-composition} and \autoref{thm:streamname-regseqrat-window-union-exhaustion} for the finite $\StreamNameUp$ window rows, and use \autoref{thm:regseqrat-common-tail-union-classifier-determinacy} for the $\RegSeqRatUp$ regularity and common-tail classifier rows. These union inputs preserve the dyadic common scale-window witness, the local $\RealUp$ terminal seal row, and the displayed support rows, and they introduce no quotient stream, selected limit, countable-choice row, or hidden completion datum.

Read the assembled union through Real L10. By \autoref{thm:real-l10-finite-section-classifier-equivalence}, the displayed $J \cup K$ surface is a single compatible four-face packet over the dyadic common scale-window witness, the finite $\StreamNameUp$ window, the $\RegSeqRatUp$ regularity and common-tail rows, and the local $\RealUp$ terminal seal row, together with the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Finally apply \autoref{thm:real-l10-exit-certificate-face-minimality}. If the displayed union carries only those four faces and support rows, minimality makes the union read the same objectwise exit certificate as the two restrictions and the ambient family. Conversely, if an additional quotient, selected-limit, choice, metric-completeness, aggregate-status, aggregate-bridge, standard-bridge, or $\RealUp$ completeness coordinate is present, it is not part of the minimal Real L10 certificate surface, so the enlarged union is no longer exactly the same objectwise exit certificate.
\end{proof}

\begin{theorem}[Real L10 finite-request sheaf exactness]
\label{thm:real-l10-finite-request-sheaf-exactness}
Let $\{\mathcal E_i\}_{i \in I}$ be a finite family of Phase $\RealUp$ and Completion packets over
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp .
$$
Let $\{J_a\}_{a \in A}$ be a finite cover of $I$ by finite request subfamilies. For each $a \in A$, let $\mathcal C_a$ be a local Phase Real and Completion exit presentation on $J_a$.

Then the family $\{\mathcal C_a\}_{a \in A}$ determines a unique objectwise Phase Real and Completion exit certificate on $I$ if and only if each $\mathcal C_a$ displays exactly the four face rows
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp,
$$
together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows, and for every finite overlap $J_{a_0}\cap\cdots\cap J_{a_m}$ the restricted presentations agree on all four face rows and on all displayed support rows.

In that case the global certificate is the objectwise restriction-gluing of the common Phase Real and Completion certificate across the finite cover. This sheaf exactness is confined to the four-face Real L10 surface. It excludes quotient streams, selected limits, countable choice, metric-completeness data, aggregate status rows, aggregate bridge rows, standard bridge rows, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
For existence, first pass to each cover member. By \autoref{thm:real-l10-finite-request-subfamily-exit-stability}, every $J_a$-presentation with the four displayed face rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows reads as the restriction of the same objectwise Phase Real and Completion certificate to that finite request subfamily.

The overlap hypotheses are exactly the compatibility data. On a binary overlap, apply \autoref{thm:real-l10-finite-request-intersection-exit-exactness}; on a finite iterated overlap, repeat the same intersection exactness along the finite meet. Thus the cover presentations agree as Real L10 sections on every retained request belonging to more than one cover member.

Now glue over the finite cover. Induct on the finite index set $A$. The empty and singleton cases are immediate from subfamily stability. For the induction step, glue the already assembled finite union to the next cover member by \autoref{thm:real-l10-finite-request-union-exit-exactness}. The overlap compatibility just proved supplies the meet datum, and the union theorem preserves exactly the four displayed faces and the displayed support rows.

It remains to identify the glued object as the Phase Real and Completion exit certificate rather than as a larger completion object. Use \autoref{thm:real-l10-finite-section-classifier-equivalence} to read the glued finite union as one compatible four-face packet, and use the RegSeqRat common-tail sheaf exactness supplied by \autoref{thm:regseqrat-common-tail-terminal-section-intersection-exactness} and \autoref{thm:regseqrat-common-tail-union-classifier-determinacy} to keep the common-tail rows objectwise on the finite cover.

For uniqueness, suppose two global exit certificates restrict to the same cover presentations. By \autoref{thm:real-l10-exit-certificate-face-minimality}, the four face rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are indispensable and exhaust the Real L10 certificate surface. Since the cover is finite and covers every request in $I$, equality on the cover members gives equality of every displayed row of the two global certificates.

Conversely, if a member omits one of the four face rows or one of the displayed support rows, minimality prevents it from being a restriction of the Real L10 exit certificate. If two presentations disagree on a finite overlap, intersection exactness prevents them from determining a single overlap certificate, so no unique global objectwise certificate can glue from the cover.

All nonescape clauses follow from the same row accounting. The proof uses only finite subfamily restriction, finite intersection exactness, finite union exactness, face minimality, and RegSeqRat common-tail exactness; none of these results adds a quotient stream, selected limit, countable-choice selector, metric-completeness datum, aggregate status row, aggregate bridge row, standard bridge row, or ambient $\RealUp$ completeness coordinate.
\end{proof}

\begin{theorem}[Real L10 finite-cover support removal obstruction]
\label{thm:real-l10-finite-cover-support-removal-obstruction}
Let $\{J_a\}_{a \in A}$ be a finite cover of a finite request family for Phase $\RealUp$ and Completion packets over
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp .
$$
For each $a \in A$, let $\mathcal C_a$ be a local Real L10 presentation on $J_a$ whose intended certificate is the finite-request sheaf certificate of \autoref{thm:real-l10-finite-request-sheaf-exactness}. If one local presentation omits any displayed support row among
$$
\BHist,\qquad \hsame,\qquad \Cont,\qquad \Pkg,\qquad \NameCert,
$$
then the finite cover cannot determine the same objectwise Real L10 exit certificate.

The failure is already witnessed on a finite cover member. It cannot be repaired by quotient streams, selected limits, countable choice, metric completeness, aggregate formalstatus rows, aggregate bridge rows, standard bridge rows, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Choose a cover member $J_a$ whose local presentation omits one displayed support row. Apply \autoref{thm:streamname-finite-cover-support-removal-global-obstruction} to the $\StreamNameUp$ finite-window component of that member: removing a displayed support coordinate leaves a finite obstruction on the cover member itself, not only after passage to the whole family.

Refinement cannot hide the omission. By \autoref{thm:streamname-finite-cover-support-invariance-under-refinement}, every finite refinement of the cover still has a member over the same request locus where the omitted support row is absent. Thus the obstruction survives finite cover subdivision and cannot be transported into a quotient-stream or selected-limit coordinate.

Now read the obstructed member through Real L10. Apply \autoref{thm:real-l10-finite-section-classifier-equivalence}: a local Real L10 section presents the objectwise certificate exactly by the dyadic common scale-window witness, the $\StreamNameUp$ finite-window section, the $\RegSeqRatUp$ regularity and common-tail classifier rows, the local $\RealUp$ terminal seal row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Minimality identifies the contradiction. By \autoref{thm:real-l10-exit-certificate-face-minimality}, none of the displayed support rows can be deleted, duplicated, detached, or replaced while the same Real L10 exit certificate is retained. Hence the obstructed local member cannot be a restriction of the same objectwise certificate.

Finally apply \autoref{thm:real-l10-finite-request-sheaf-exactness}. A finite cover determines the global Real L10 certificate only when every cover member displays all four face rows and all five support rows, with overlap agreement on those rows. Since one member lacks a required support row, the exactness criterion fails on that member. The listed completion, choice, status, bridge, and $\RealUp$ completeness data are outside the finite certificate surface identified above, so they provide no repair coordinate.
\end{proof}

\begin{theorem}[Real L10 finite-cover face removal obstruction]
\label{thm:real-l10-finite-cover-face-removal-obstruction}
Let $\{J_a\}_{a \in A}$ be a finite cover of a finite request family for Phase $\RealUp$ and Completion packets over
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp .
$$
For each $a \in A$, let $\mathcal C_a$ be a local Real L10 presentation on $J_a$ whose intended certificate is the finite-request sheaf certificate of \autoref{thm:real-l10-finite-request-sheaf-exactness}. If one local presentation omits any one of the four face rows
$$
\DyadicRatCoreUp,\qquad \StreamNameUp,\qquad \RegSeqRatUp,\qquad \RealUp,
$$
then the finite cover cannot determine the same objectwise Real L10 exit certificate.

The obstruction is a face-row obstruction, not a support-row obstruction in disguise. It cannot be repaired by quotient streams, selected limits, countable choice, metric-completeness data, aggregate status rows, aggregate bridge rows, standard bridge rows, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Choose a cover member $J_a$ whose local presentation omits one of the four displayed face rows. By \autoref{thm:real-l10-finite-request-sheaf-exactness}, a finite cover determines the global Real L10 certificate only when every cover member displays all four face rows and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows, with overlap agreement on those rows.

The missing face is indispensable. Apply \autoref{thm:real-l10-exit-certificate-face-minimality}. Deleting the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, or local $\RealUp$ row removes one object of the four-face certificate, so the obstructed local member cannot be a restriction of the same objectwise Real L10 exit certificate.

The StreamName and RegSeqRat boundary clauses give the same obstruction on the two middle faces. Apply \autoref{thm:streamname-open-phase-four-face-minimality} to the $\StreamNameUp$ open-phase row, and apply \autoref{thm:regseqrat-real-terminal-four-face-exactness} to the $\RegSeqRatUp$ and local $\RealUp$ terminal rows. These results keep the finite-window, common-tail, and terminal-seal data attached to the displayed object faces rather than to an external completion coordinate.

Finally return to the finite cover. Since one cover member lacks a required face row, the exactness criterion of \autoref{thm:real-l10-finite-request-sheaf-exactness} fails before any global certificate can be glued. Quotient streams, selected limits, countable-choice selectors, metric-completeness data, aggregate status rows, aggregate bridge rows, standard bridge rows, and ambient $\RealUp$ completeness are not rows of the finite Real L10 certificate surface, so they provide no replacement for the deleted face.
\end{proof}
