\begin{theorem}[Real constant embedding terminal four-face consumption]
\label{thm:real-constant-embedding-terminal-four-face-consumption}
The concrete constant rational embedding
$$
d\longmapsto (\mathsf{RatConstStream}_d,\Eone(d))
$$
from \autoref{thm:real-constant-rational-embedding-certificate} is accepted
as a $\RealUp$ public seal read only through the four Phase Real and Completion
faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
Its visible support rows are precisely the $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows carried by those faces. The consumption route
therefore exports no quotient stream equality, selected host limit, ambient
completeness row, metric-completeness datum, countable choice, or standard
bridge row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:real-constant-rational-embedding-certificate}. It
packages the hidden rational seed $d$, the constant stream
$\mathsf{RatConstStream}_d$, and the e-one seal $\Eone(d)$ as one concrete
$\BHist$-anchored rational-to-real name.

Apply \autoref{thm:regseqrat-constant-real-seal-handoff}. The same constant
source reaches the local $\RealUp$ seal only after the constant
$\StreamNameUp$ schedule, the $\DyadicRatCoreUp$ endpoint and radius rows, and
the $\RegSeqRatUp$ regularity and classifier ledger have been read through
their displayed support rows.

Next apply \autoref{thm:streamname-realup-constant-observation-handoff}. This
keeps the constant observation surface at the pointwise StreamName boundary
and leaves regularity, dyadic seal data, and the Real seal classifier as
downstream obligations rather than additional source coordinates.

Finally use \autoref{thm:real-open-phase-four-object-terminal-route}. That
terminality theorem reads every accepted public seal or completion-facing
route through exactly the four displayed faces with $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ support. Hence the constant rational
embedding is consumed by the same terminal four-face boundary, and the excluded
quotient, selected-limit, completeness, choice, metric-completeness, and
standard-bridge rows cannot replace any face of the route.
\end{proof}

\begin{theorem}[Real constant embedding terminal four-face pullback]
\label{thm:real-constant-embedding-terminal-four-face-pullback}
Any two accepted presentations of the concrete constant rational embedding
which agree on the displayed
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
faces and on the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows determine the same public $\RealUp$ seal route. Conversely, any terminal
four-face packet with those support rows determines the constant embedding
seal read.

The pullback exports no quotient stream equality, selected host limit,
ambient $\RealUp$ completeness, metric completeness, countable choice, or
standard bridge row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-constant-embedding-terminal-four-face-consumption}. Each
accepted presentation of the constant rational embedding is already consumed
only through the four displayed faces and the shared $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows.

Next use \autoref{thm:regseqrat-constant-real-seal-handoff}. Agreement on the
constant $\DyadicRatCoreUp$ endpoint data, the constant $\StreamNameUp$
schedule, and the $\RegSeqRatUp$ regularity and classifier ledger gives one
visible handoff surface for the $\RealUp$ seal.

Apply \autoref{thm:streamname-realup-constant-observation-handoff}. This keeps
the constant observation at the pointwise StreamName boundary and leaves the
dyadic, regularity, and Real seal rows as the downstream four-face packet
rather than as extra source coordinates.

Finally invoke \autoref{thm:real-open-phase-four-object-terminal-route}. Two
accepted reads that agree on the four faces and the listed support rows have
the same terminal finite route to the public $\RealUp$ seal. In the reverse
direction, a terminal packet carrying exactly those faces and support rows is
therefore read as the constant embedding seal route supplied by the handoff
theorems. Since none of the cited packets carries quotient stream equality,
selected host limits, ambient completeness, metric completeness, countable
choice, or a standard bridge row, no such row can replace any face of the
pullback.
\end{proof}

\begin{theorem}[Real constant embedding terminal four-face classifier preservation]
\label{thm:real-constant-embedding-terminal-four-face-classifier-preservation}
Suppose two accepted presentations of the concrete constant rational embedding
agree on the $\DyadicRatCoreUp$ endpoint and radius rows, the constant-window
$\StreamNameUp$ row, the $\RegSeqRatUp$ regularity and classifier ledger, and
the local $\RealUp$ seal classifier. Then their public $\RealUp$ classifier
read is the same terminal four-face classifier route through
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
Conversely, any accepted terminal four-face classifier route carrying those
support rows determines the classifier read of the constant rational embedding.

This classifier preservation statement exports no quotient stream equality,
selected host limit, host real equality, ambient completeness,
metric-completeness data, countable choice, or standard bridge row.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-constant-embedding-terminal-four-face-consumption}. It
confines the accepted constant rational embedding to the displayed four faces,
so the classifier question can only inspect the dyadic endpoint and radius
rows, the constant StreamName window, the RegSeqRat ledger, and the local
Real seal classifier.

Next use
\autoref{thm:real-constant-embedding-terminal-four-face-pullback}. Agreement
on those four faces and their $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ support rows gives one terminal route for the public $\RealUp$
seal read, and every accepted terminal packet with the same support rows reads
back to that constant embedding route.

Now transport the classifier data along the two handoff boundaries. Apply
\autoref{thm:regseqrat-constant-real-seal-handoff} to identify the
$\RegSeqRatUp$ regularity and classifier ledger that reaches the Real seal,
and apply \autoref{thm:streamname-realup-constant-observation-handoff} to
keep the constant observation boundary at the StreamName window.

Finally invoke \autoref{thm:real-l10-four-face-classifier-pullback}. The L10
classifier pullback identifies classifier equality on an accepted four-face
route from exactly the displayed classifier rows. Thus the two presentations
have the same public $\RealUp$ classifier read, and the reverse terminal route
determines the classifier read of the constant rational embedding. The
excluded quotient, selected-limit, host-real, completeness, choice,
metric-completeness, and standard-bridge rows are absent from every cited
route, so they cannot supply an alternative classifier preservation path.
\end{proof}

\begin{theorem}[Real terminal four-face no direct seal collapse]
\label{thm:real-terminal-four-face-no-direct-seal-collapse}
If a public $\RealUp$ classifier read of the concrete constant rational
embedding is accepted, then it factors through the displayed
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
faces with the shared $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows. Conversely, a packet which omits any of the first three faces is not an
accepted public classifier read of the constant embedding.

Thus the terminal public read excludes quotient stream equality, selected
limits, host real equality, countable choice, ambient completeness, metric
completeness, standard bridge rows, and any direct $\RealUp$ seal edge around
the dyadic, stream, or regular-sequence faces.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-constant-embedding-terminal-four-face-consumption}. It gives
the route inventory for every accepted constant-embedding public seal read:
the dyadic core, stream name, regular sequence, and Real faces are all visible,
and their only support rows are the common $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ rows.

Next use
\autoref{thm:real-constant-embedding-terminal-four-face-pullback}. The pullback
identifies the public seal route uniquely from precisely those faces and rows.
Hence a purported public read that bypasses $\DyadicRatCoreUp$,
$\StreamNameUp$, or $\RegSeqRatUp$ has no route coordinate from which the
constant embedding seal can be pulled back.

Finally apply
\autoref{thm:real-constant-embedding-terminal-four-face-classifier-preservation}.
Classifier preservation transports the same uniqueness statement from the seal
route to the public classifier read. Therefore an accepted classifier read
factors through all four faces, while a packet missing any of the first three
faces is not an accepted constant-embedding classifier read. The excluded
quotient stream, selected-limit, host-real, choice, ambient-completeness,
metric-completeness, standard-bridge, and direct-seal data are absent from the
three cited routes, so none of them supplies a replacement edge to $\RealUp$.
\end{proof}

\begin{theorem}[Real constant embedding four-face classifier terminality]
\label{thm:real-constant-embedding-four-face-classifier-terminality}
For any two accepted concrete constant rational embedding classifier reads,
equality of their public $\RealUp$ classifier reads holds exactly when their
visible terminal rows agree: the $\DyadicRatCoreUp$ endpoint and radius rows,
the constant-window $\StreamNameUp$ row, the $\RegSeqRatUp$ regularity and
classifier ledger, the local $\RealUp$ seal classifier, and the shared
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.

Conversely, any terminal four-face classifier packet carrying precisely those
rows determines the public classifier read of the concrete constant rational
embedding. This terminality criterion exports no quotient stream equality, host
real equality, selected limit, countable choice, ambient completeness,
metric-completeness row, standard bridge row, or direct $\RealUp$ seal bypass.
\end{theorem}
\begin{proof}
For the forward direction, start with the accepted public classifier equality
and apply
\autoref{thm:real-constant-embedding-terminal-four-face-classifier-preservation}.
Classifier preservation restricts the equality test to the displayed four
faces. Then use
\autoref{thm:real-terminal-four-face-no-direct-seal-collapse}: an accepted
classifier read cannot pass directly to $\RealUp$ while omitting the dyadic,
stream, or regular-sequence faces.

It remains to extract the rows that witness the equality. Apply
\autoref{thm:real-constant-embedding-terminal-four-face-pullback}. The pullback
identifies the public seal route from the $\DyadicRatCoreUp$ endpoint and
radius rows, the constant-window $\StreamNameUp$ row, the $\RegSeqRatUp$ ledger,
the local $\RealUp$ classifier row, and the common $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ support. Hence equality of the public classifier read
forces agreement on exactly those rows.

For the reverse direction, begin with agreement on the listed terminal rows.
The pullback theorem repacks those rows as one terminal four-face packet for the
constant embedding seal route. Classifier preservation then transports that
repacked packet to the public $\RealUp$ classifier read, so the two accepted
presentations have the same classifier endpoint.

The same two theorems also give the converse packet clause: a terminal
four-face classifier packet with precisely the displayed rows determines the
constant embedding classifier read. The no-direct-seal-collapse theorem excludes
quotient stream equality, host real equality, selected limits, countable choice,
ambient or metric completeness, standard bridges, and direct Real seal bypasses
from serving as an alternative terminal endpoint.
\end{proof}
