The current $\RealUp$ L10 carrier is read through the $\StreamNameUp$ finite observation interface of \autoref{ch:concrete-instances-streamname-namecert} and the $\RegSeqRatUp$ regularity certificate of \autoref{ch:concrete-instances-regseqrat-namecert}. The later $\MetricSpaceUp$ consumer in \autoref{ch:concrete-instances-metric-namecert} uses the resulting $\RealUp$-valued distance interface only after those two sibling certificates are present, so the Real route is a sibling lattice through StreamName and rational regular sequences before it becomes a metric-distance surface.

\begin{theorem}[Real StreamName RegSeqRat metric-observation factorization]
\label{thm:real-streamname-regseqrat-metric-observation-factorization}
Every $\MetricSpaceUp$-facing observation of an accepted $\RealUp$
finite-window carrier factors through the ordered BEDC observation route
$$
\StreamNameUp \to \RegSeqRatUp \to \RealUp \to
\mathsf{MetricDistanceWitness}.
$$
The first leg reads only the $\StreamNameUp$ finite observation interface and
its displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The
second leg reads the $\RegSeqRatUp$ regularity rows together with the dyadic
window rows that lock the finite rational schedule. The third leg exposes the
local $\RealUp$ seal and readback surface. Only after that seal is visible may
the downstream $\MetricSpaceUp$ consumer read the
$\mathsf{MetricDistanceWitness}$ ledger.

Thus the metric observation exports no quotient Cauchy class, host real
equality, ambient completeness principle, or direct metric access to an
unsealed stream.
\end{theorem}
\begin{proof}
Start with \autoref{thm:real-dyadic-stream-regseq-route}. It places the
accepted Real-facing read on the route from dyadic observations through
$\StreamNameUp$ finite windows and $\RegSeqRatUp$ regular readback to the
local $\RealUp$ seal, using only the displayed $\BHist$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows.

Next apply \autoref{thm:streamname-real-regseq-finite-window-handoff} and
\autoref{thm:regseqrat-streamname-dyadic-window-lock}. The handoff fixes the
finite StreamName observation interface, while the lock identifies the
regular-rational rows with the dyadic finite-window schedule consumed by
$\RegSeqRatUp$.

Now use \autoref{thm:real-l10-metric-boundary-nonescape}. It keeps every
metric-facing read outside the Real construction boundary until the local
$\RealUp$ seal and readback surface are already visible.

Finally apply the metric witness ledger only at the downstream consumer
boundary, as in \autoref{thm:metric-distance-witness-cont-depth-add}. This
records the $\mathsf{MetricDistanceWitness}$ depth accounting after the Real
seal is available, and it supplies no coordinate for quotient Cauchy classes,
host real equality, ambient completeness, or direct metric access to an
unsealed stream.
\end{proof}

\begin{theorem}[Real StreamName RegSeqRat metric classifier correspondence]
\label{thm:real-streamname-regseqrat-metric-classifier-correspondence}
Every accepted metric-facing $\RealUp$ finite-window observation is
classifier-determined by the ordered BEDC route
$$
\StreamNameUp\text{ finite-window classifier}\to
\RegSeqRatUp\text{ regularity classifier}\to
\RealUp\text{ seal classifier}\to
\mathsf{MetricDistanceWitness}.
$$
The $\StreamNameUp$ leg fixes the finite schedule and its displayed $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The $\RegSeqRatUp$ leg fixes
the regularity classifier over the same window rows. The $\RealUp$ leg seals the
readback surface before the metric witness can be consulted.

Conversely, a $\mathsf{MetricDistanceWitness}$ read cannot identify two
$\RealUp$ observations unless their $\StreamNameUp$ schedules and
$\RegSeqRatUp$ windows reach the same $\RealUp$ seal. The correspondence
therefore exports no quotient Cauchy class, host real equality, ambient
completeness principle, or direct metric access to an unsealed stream.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-streamname-regseqrat-metric-observation-factorization}. It
places every accepted metric-facing observation on the ordered route from
$\StreamNameUp$ finite windows through $\RegSeqRatUp$ regularity and the
$\RealUp$ seal before the $\mathsf{MetricDistanceWitness}$ ledger is read.

Next use
\autoref{thm:streamname-regseqrat-real-open-phase-dependency-lattice}. The
dependency lattice says that reaching the RegSeqRat readback and Real seal
surfaces from a finite StreamName window exposes only the displayed finite
route and its $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Then apply \autoref{thm:regseqrat-l10-source-lattice-pointer}. It identifies
the L10 source owners of the schedule, dyadic endpoint rows, regularity rows,
classifier rows, and terminal Real seal. Thus the StreamName classifier and the
RegSeqRat classifier determine the Real-facing seal read rather than leaving a
free ambient coordinate.

Finally use \autoref{thm:metric-distance-witness-cont-depth-add}. The metric
consumer can perform its continuation-depth accounting only after the sealed
Real read is already present. Therefore a metric witness cannot separate or
identify Real observations through any coordinate beyond the shared finite
schedule, regularity window, and Real seal; quotient Cauchy classes, host real
equality, ambient completeness, and direct access to an unsealed stream remain
off the route.
\end{proof}

\begin{theorem}[Real L10 metric classifier pullback correspondence]
\label{thm:real-l10-metric-classifier-pullback-correspondence}
Let $R$ and $S$ be accepted metric-facing $\RealUp$ finite-window
observations. Agreement of their $\mathsf{MetricDistanceWitness}$ classifiers
is equivalent to agreement of the displayed four-face route consisting of the
$\DyadicRatCoreUp$ endpoint, radius, and distance ledger, the $\StreamNameUp$
finite-window schedule, the $\RegSeqRatUp$ regularity and common-tail
classifier rows, the local $\RealUp$ seal classifier row, and the support rows
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

This pullback correspondence does not expose quotient stream equality, host
real equality, selected limits, countable choice, ambient completeness,
metric-completeness rows, standard bridge rows, or direct metric access to an
unsealed stream.
\end{theorem}
\begin{proof}
For the forward direction, first apply
\autoref{thm:real-streamname-regseqrat-metric-classifier-correspondence}. It
reads agreement of the metric witness classifier back through the
$\StreamNameUp$ schedule, the $\RegSeqRatUp$ regularity window, and the local
$\RealUp$ seal before any downstream metric ledger is consulted.

Then apply
\autoref{thm:real-common-tail-terminal-four-face-classifier-equivalence}. The
terminal common-tail comparison identifies the same classifier agreement with
agreement of the $\RegSeqRatUp$ common-tail packet, the $\StreamNameUp$
terminal-window packet, the $\DyadicRatCoreUp$ endpoint, radius, and distance
ledger, the local $\RealUp$ seal-source row, and the displayed support rows.

Finally use \autoref{thm:real-l10-four-face-classifier-sheaf-condition}. It
keeps the local agreements compatible on finite covers, so the metric-facing
classifier read is exactly the four-face classifier surface rather than an
extra metric coordinate.

For the reverse direction, assume the two observations agree on the displayed
four-face route and on the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$. Repack those rows through
\autoref{thm:real-l10-four-face-finite-pullback-public-interface}; the result
is one public finite pullback interface over $\DyadicRatCoreUp$,
$\StreamNameUp$, $\RegSeqRatUp$, and the local $\RealUp$ seal.

With the Real seal visible, apply
\autoref{thm:real-streamname-regseqrat-metric-classifier-correspondence} again
to identify the sealed classifier route seen by the metric consumer. Only at
this point may \autoref{thm:metric-distance-witness-cont-depth-add} be used:
it records continuation-depth accounting for the already sealed distance
witness and adds no quotient stream equality, host real equality, selected
limit, choice, completeness, standard bridge, or unsealed-stream row.
\end{proof}

\begin{theorem}[Real L10 metric pre-seal non-escape]
\label{thm:real-l10-metric-preseal-nonescape}
Let $R$ be an accepted metric-facing $\RealUp$ finite-window observation. Suppose
the $\mathsf{MetricDistanceWitness}$ classifier of $R$ agrees with the displayed
four-face route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, the
local $\RealUp$ seal classifier, and the support rows $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$. Then the sealed $\RealUp$ boundary contains no
BEDC coordinate for quotient stream equality, selected limits, countable choice,
host real equality, ambient Real completeness, metric-completeness rows,
standard bridge rows, or direct access to an unsealed stream.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:real-streamname-regseqrat-metric-observation-factorization}. It
places the metric-facing observation on the ordered route through
$\StreamNameUp$, $\RegSeqRatUp$, the local $\RealUp$ seal, and only then the
$\mathsf{MetricDistanceWitness}$ ledger.

Next use
\autoref{thm:real-streamname-regseqrat-metric-classifier-correspondence}. The
metric witness classifier is read back through the finite StreamName schedule,
the RegSeqRat regularity classifier, and the Real seal classifier, so the
classifier agreement has no independent metric-side carrier.

Now apply
\autoref{thm:real-l10-metric-classifier-pullback-correspondence}. It identifies
that classifier agreement with the four-face pullback over
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, the local $\RealUp$ seal,
and the displayed support rows.

The non-escape conclusion is exactly the boundary statement of
\autoref{thm:real-l10-metric-boundary-nonescape}: before the sealed Real
readback is present, there is no BEDC coordinate for quotient stream equality,
selected limits, countable choice, host real equality, ambient Real
completeness, metric-completeness rows, standard bridge rows, or direct access
to an unsealed stream.

After that boundary is fixed,
\autoref{thm:metric-distance-witness-cont-depth-add} may be cited only as the
downstream continuation-depth ledger. It records metric consumer depth after the
sealed Real route is already visible and does not add any of the excluded
metric-side completion or choice data.
\end{proof}

\begin{theorem}[Real L10 metric witness facewise determinacy]
\label{thm:real-l10-metric-witness-facewise-determinacy}
Let $R$ and $S$ be accepted metric-facing $\RealUp$ finite-window observations.
Their $\mathsf{MetricDistanceWitness}$ classifier reads agree exactly when the
displayed four-face route agrees: the $\DyadicRatCoreUp$ endpoint, radius, and
distance ledger; the $\StreamNameUp$ finite-window schedule; the $\RegSeqRatUp$
regularity and common-tail classifier rows; the local $\RealUp$ seal classifier;
and the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Conversely, componentwise agreement of those four faces and support rows
supplies the same $\mathsf{MetricDistanceWitness}$ classifier read. This
determinacy statement exports no quotient stream equality, selected limit,
countable choice, host real equality, ambient completeness,
metric-completeness row, standard bridge row, or direct access to an unsealed
stream.
\end{theorem}
\begin{proof}
For the forward direction, apply
\autoref{thm:real-streamname-regseqrat-metric-observation-factorization}. It
routes each accepted metric-facing observation through the $\StreamNameUp$
finite-window interface, the $\RegSeqRatUp$ regularity surface, the local
$\RealUp$ seal, and only then the $\mathsf{MetricDistanceWitness}$ ledger.

Next use
\autoref{thm:real-streamname-regseqrat-metric-classifier-correspondence}. The
metric classifier readback is therefore a readback of the StreamName,
RegSeqRat, and Real seal classifiers, not a separate metric-side coordinate.
Together with \autoref{thm:streamname-l10-four-face-exit-gate}, this places the
Real consumer on the sibling L10 exit gate over the displayed four faces.

Now apply
\autoref{thm:real-l10-metric-classifier-pullback-correspondence}. It identifies
agreement of the metric witness classifiers with agreement of the
$\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and local $\RealUp$ seal
faces, together with the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$.

For the reverse direction, start with componentwise agreement on those four
faces and support rows. The same pullback correspondence repacks that data as
agreement of the sealed Real-facing classifier route, and the classifier
correspondence then supplies the identical
$\mathsf{MetricDistanceWitness}$ read.

Finally apply \autoref{thm:real-l10-metric-preseal-nonescape}. The facewise
agreement has no coordinate for quotient stream equality, selected limit,
countable choice, host real equality, ambient completeness, metric-completeness
rows, standard bridge rows, or direct unsealed-stream access, so the theorem
states only determinacy of the finite classifier route.
\end{proof}
