\section{Real L10 machine-admissible minimal basis}
\label{sec:real-l10-machine-admissible-minimal-basis}

\begin{theorem}[Real L10 machine-admissible minimal basis]
\label{thm:real-l10-machine-admissible-minimal-basis}
Let $S$ be a terminal $\RealUp$ seal section for the current Phase Real and Completion exit over the ordered route
$$
\DyadicRatCoreUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp .
$$
Then $S$ is machine-admissible for that exit if and only if the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff read one common four-face certificate over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

These three touchpoints form the minimal machine-facing basis. Deleting the StreamName singleton finite-window handoff loses the finite-window face, deleting the DyadicRatCore RegSeqRat bridge handoff exactness loses the endpoint and tolerance ledger as transported to the RegSeqRat classifier and transport rows, and deleting the RegSeqRat Real seal handoff loses the terminal $\RealUp$ seal face. No aggregate formalstatus row, aggregate bridge row, quotient stream, selected limit, countable-choice row, host equality row, metric-completeness row, standard bridge row, or ambient $\RealUp$ completeness coordinate belongs to the basis.
\end{theorem}
\begin{proof}
For the forward direction, apply \autoref{thm:real-terminal-seal-machine-route-exhaustion}. It identifies the machine-facing support of a terminal $\RealUp$ seal section with exactly the StreamName singleton finite-window handoff, the DyadicRatCore RegSeqRat bridge handoff exactness, and the RegSeqRat Real seal handoff, all reading the same four-face certificate over the displayed construction faces and support rows.

For the reverse direction, apply \autoref{thm:real-l10-four-face-exit-criterion-equivalence}. A common read by the three named machine touchpoints is precisely the finite packet required for the Phase $\RealUp$ and Completion exit criterion. Then use \autoref{thm:streamname-open-phase-lean-touchpoint-triad} and \autoref{thm:streamname-real-completion-exit-lean-route-boundary} to place that packet on the machine-facing route.

It remains to prove minimality. The StreamName touchpoint triad supplies the singleton finite-window handoff and therefore the finite-window face. The DyadicRatCore touchpoint-completeness theorem, \autoref{thm:dyadicratcore-l10-exit-lean-touchpoint-completeness}, supplies the endpoint and tolerance ledger as the exact bridge into the RegSeqRat classifier and transport rows. The StreamName Real-completion boundary supplies the RegSeqRat Real seal handoff and therefore the terminal $\RealUp$ face.

Finally combine these minimality reads with \autoref{thm:real-four-face-machine-touchpoint-minimality}. Any deletion of one of the three named touchpoints removes one displayed face or one support route row from the accepted machine read, while the cited route-exhaustion and boundary theorems provide no constructor for aggregate status, bridge, quotient, selected-limit, choice, equality, metric-completeness, or ambient completeness coordinates.
\end{proof}
