The $\RealSeparabilityUp$ Cauchy-setoid modulus route records the density-side dependency that keeps regular rational names comparable before a countable dense handoff is claimed. It reads \autoref{ch:concrete-instances-regseqrat-namecert} for finite regular windows, \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert} for the classifier that identifies equivalent regular Cauchy presentations, and the RealUp L10 input factorization before exporting a density route.

\begin{theorem}[Real separability Cauchy setoid route]
\label{thm:real-separability-cauchy-setoid-route}
Every $\RealSeparabilityUp$ density read that consumes $\RegSeqRatUp$ regular names factors through the $\CauchyEquivalenceSetoidUp$ classifier before it claims a countable dense route. The consumer may then use the RealUp L10 route, but only after the regular readback, Cauchy-equivalence classifier, dyadic tolerance, terminal seal, transport, replay, provenance, and local naming rows are visible; it exports no quotient real equality, selected dense enumeration, host equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the regular rational names. A density read that consumes $\RegSeqRatUp$ data first opens the finite windows and dyadic tolerances described by \autoref{ch:concrete-instances-regseqrat-namecert}; those rows are not yet a Real-facing countable dense route.

Next pass through the Cauchy-equivalence classifier of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}. Equivalent regular Cauchy presentations replay the same density read only through the displayed classifier row, so the consumer cannot replace the route by quotient real equality or a selected representative.

Finally use the RealUp L10 input factorization. The factorization keeps the terminal Real seal downstream from finite stream windows, regular readback, and dyadic tolerance data, so the countable dense route is claimed only after the setoid comparison has already fixed the regular-name boundary.
\end{proof}
