\begin{lemma}[RealSeparability countable dense route]
\label{lem:real-separability-countable-dense-route}
Every $\RealSeparabilityUp$ density read that is exported as a countable dense surface factors through the countable dense subset boundary of \autoref{ch:concrete-instances-countable-dense-subset-namecert}, the dyadic-density witness surface of \autoref{ch:concrete-instances-dyadic-density-real-namecert}, and the rational-density witness surface of \autoref{ch:concrete-instances-rational-density-real-namecert} before reaching any terminal $\RealUp$ seal.

The route reads the displayed rational enumeration, dyadic tolerance, finite $\StreamNameUp$ window, regular rational readback, and local $\NameCert_{\RealSeparabilityUp}$ rows as one finite dependency chain. It exports no host dense subset, selected nearest point, quotient real equality, countable-choice selector, or ambient completeness coordinate.
\end{lemma}
\begin{proof}
Project the accepted $\RealSeparabilityUp$ carrier to its rational enumeration, dyadic tolerance, finite window, regular readback, Real seal, exactness ledger, transport, replay, provenance, and local naming rows. The countable dense subset boundary supplies only the displayed indexed dense-source row, so the separability read first cites \autoref{ch:concrete-instances-countable-dense-subset-namecert}.

The tolerance and witness rows then pass through the two density siblings. The dyadic-density surface of \autoref{ch:concrete-instances-dyadic-density-real-namecert} supplies the dyadic tolerance witness, and the rational-density surface of \autoref{ch:concrete-instances-rational-density-real-namecert} supplies the rational interval witness.

Finally the existing $\RealSeparabilityUp$ route consumes those witnesses through the finite $\StreamNameUp$ window and $\RegSeqRatUp$ readback before the terminal $\RealUp$ seal. Since every row is displayed in that chain, no host dense subset, selected nearest point, quotient equality, choice selector, or ambient completeness object is available.
\end{proof}
