\begin{theorem}[Real separability compact-continuous sup-norm forward link]
\label{thm:real-separability-continuous-sup-norm-forward-link}
Every compact-continuous sup-norm or uniform-modulus consumer of an accepted $\RealSeparabilityUp$ density packet first reads the displayed dyadic-density route, the $\RegSeqRatUp$ readback rows, the finite $\StreamNameUp$ windows, the terminal $\RealUp$ seal, and the compact-uniform surfaces of \autoref{ch:concrete-instances-compactuniformcontinuity-namecert} and \autoref{ch:concrete-instances-uniformmodulus-namecert}. In particular, the consumer may reach \autoref{ch:concrete-instances-continuous-sup-norm-namecert} only through those finite density, readback, window, Real-seal, compact-continuity, and modulus rows.

The forward link exports no selected dense point, host dense subset, quotient Real equality, open-cover compactness, selected supremum, countable-choice search, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-separability-carrier}. Its rows expose the rational source, dyadic tolerance ledger, StreamName windows, regular rational readback, terminal Real seal, density exactness, transport, replay, provenance, and local naming.

Use the existing dyadic-density and RegSeqRat routes. They keep every density request on the finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ surface before any compact-continuous consumer can inspect the data.

Now pass to the compact-uniform route. The compact-continuity and uniform-modulus packets consume only displayed finite windows, modulus ledgers, and Real-sealed comparison rows, and the $\ContinuousSupNormUp$ packet reads those rows as its finite bound source.

Thus the separability packet supplies a dependency edge to compact-continuous norm and modulus consumers only through the named BEDC rows. The excluded host dense subset, selected point, quotient equality, open-cover, supremum, choice, and completeness objects are absent from the route.
\end{proof}
