\begin{theorem}[RealSeparability RegSeqRat density pullback]
\label{thm:real-separability-regseqrat-density-pullback}
Every $\RealSeparabilityUp$ countable-density export factors first through the $\RegSeqRatUp$ finite-window readback and the dyadic-density witness before it reaches the terminal $\RealUp$ seal. In particular, the dependency route of \autoref{thm:real-separability-regseqrat-dependency} and the countable dense route of \autoref{lem:real-separability-countable-dense-route} force each exported dense read to display its regular rational window, dyadic tolerance witness, and Real seal boundary; no host dense subset, countable-choice selector, or ambient completeness coordinate can supply the density export.
\end{theorem}
\begin{proof}
Project the accepted $\RealSeparabilityUp$ carrier. Its density row can expose only the displayed rational or dyadic schedules, finite readback rows, Real-facing seal, transport, replay, provenance, and local naming data.

Use the RegSeqRat dependency of \autoref{thm:real-separability-regseqrat-dependency}. It places the finite-window readback before any Real-facing separability export, so the density read cannot start from an untracked host subset.

Next use the dyadic-density sibling route and \autoref{lem:real-separability-countable-dense-route}. The dyadic witness supplies the tolerance row consumed by the countable dense schedule before the terminal $\RealUp$ seal is read.

Thus the Real seal receives only the displayed RegSeqRat windows, dyadic witness, and certificate rows. Since the carrier has no coordinate for a host dense subset, choice selector, or ambient completeness theorem, every countable-density export factors through the stated pullback route.
\end{proof}
