\begin{theorem}[Real separability RegSeqRat dependency]
\label{thm:real-separability-regseqrat-dependency}
Every $\RealSeparabilityUp$ density read consumes the finite $\RegSeqRatUp$ window route and the dyadic-density witness before it exports separability. The read first reaches the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}, then routes the requested rational approximation through \autoref{ch:concrete-instances-regseqrat-namecert}, and finally checks the tolerance witness through \autoref{ch:concrete-instances-dyadic-density-real-namecert}. The resulting separability observation is therefore a finite regular-sequence and dyadic-density handoff, not a host dense-subset assertion, selected nearest point, quotient stream, or ambient completeness claim.
\end{theorem}
\begin{proof}
Project the accepted $\RealSeparabilityUp$ carrier through the local density route. The Real-facing consumer can only read the terminal $\RealUp$ seal after the rational enumeration, dyadic tolerance, StreamName window, and regular rational readback rows have been displayed.

The $\RegSeqRatUp$ row supplies the finite-window readback. It carries the inspected rational candidate and the opened observation window as regular sequence data, so the separability consumer does not receive a detached host rational point.

The dyadic-density sibling then supplies the tolerance witness. It binds the displayed dyadic scale to the same Real-facing request before any separability row is exported.

The structural $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows replay only those displayed rows. Since none of the routes contains a coordinate for a host dense subset, selected nearest point, quotient stream, or ambient completeness, every $\RealSeparabilityUp$ density read depends on the RegSeqRat finite-window route and dyadic-density witness before export.
\end{proof}
