\begin{theorem}[RealSeparability dense Real forward link]
\label{thm:real-separability-real-density-forward-link}
Every accepted $\RealSeparabilityUp$ dense finite schedule that exposes $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows feeds both the $\PolishSpaceUp$ countable dense surface of \autoref{ch:concrete-instances-polishspace-namecert} and the $\SeparatedCompletionUp$ zero-distance completion route of \autoref{ch:concrete-instances-separatedcompletion-namecert}. The forward link carries only displayed finite schedules, stream windows, regular rational readbacks, dyadic tolerances, and Real seals; it does not select dense points, invoke countable choice, identify quotient completion classes, or use ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted $\RealSeparabilityUp$ schedule. Its dense rows are finite: a consumer sees named windows, regular rational readbacks, dyadic tolerance comparisons, and terminal Real seals before any dense-surface claim is public.

For the PolishSpace branch, read the same finite schedule as a countable dense surface. The route supplies a displayed dense inventory to the $\PolishSpaceUp$ consumer, but no point is selected outside the schedule and no countable-choice operator is introduced.

For the SeparatedCompletion branch, pass the Real-seal comparisons through the zero-distance completion route. The $\SeparatedCompletionUp$ consumer reads the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ evidence before the separated classifier is available.

The two branches therefore share one dense Real source. Since the carrier has no coordinate for chosen dense points, quotient completion equality, countable choice, or ambient completeness, the forward link is exhausted by the displayed finite RealSeparability route.
\end{proof}
