\begin{theorem}[Real separability dyadic density forward link]
\label{thm:real-separability-dyadic-density-forward-link}
Every $\RealSeparabilityUp$ density route that consumes a dyadic-density witness must pass that witness through the finite $\RegSeqRatUp$ readback surface and the regular Cauchy completion route before it exports a separability ledger. In particular, the dyadic witness of \autoref{ch:concrete-instances-dyadic-density-real-namecert} and \autoref{thm:real-separability-dyadic-density-dependency}, the RegSeqRat dependency of \autoref{thm:real-separability-regseqrat-dependency}, the regular Cauchy completion criterion route of \autoref{thm:regular-cauchy-completion-criterion-real-separability-route}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert} form one displayed dependency chain rather than four detachable facts.

The exported separability ledger therefore records a finite dyadic-density route through $\DyadicRatCoreUp$, $\RegSeqRatUp$, regular Cauchy completion, and $\RealUp$. It does not select nearest dyadics, identify quotient Real representatives, invoke ambient completeness, or detach the dense set from the displayed regular-rational readback route.
\end{theorem}
\begin{proof}
Start with the dyadic-density dependency. Theorem~\ref{thm:real-separability-dyadic-density-dependency} exposes the dyadic witness only through a finite tolerance row and a regular rational observation window.

Next read the RegSeqRat route. Theorem~\ref{thm:real-separability-regseqrat-dependency} keeps that witness on the displayed regular-rational surface before any $\RealSeparabilityUp$ ledger is exported.

Now pass through regular Cauchy completion. Theorem~\ref{thm:regular-cauchy-completion-criterion-real-separability-route} consumes the same finite dyadic and regular-rational rows before the terminal $\RealUp$ seal is read.

Thus the separability ledger receives one finite dependency chain through dyadic density, RegSeqRat readback, regular Cauchy completion, and Real sealing. Since none of those rows is a nearest-point selector, quotient-real equality, ambient completeness theorem, or detached dense subset, the forward link exports only the displayed separability route.
\end{proof}
