\begin{theorem}[RealSeparability L10 source route]
\label{thm:real-separability-l10-source-route}
Every $\RealSeparabilityUp$ consumer that reads finite dense-window data through the L10 source chain must display the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows cited by \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The route exposes finite stream windows, regular rational sequence readback, dyadic tolerance control, and the terminal Real seal before any separability-density handoff is consumed.
\end{theorem}

\begin{proof}
Project the RealSeparability packet through its displayed density route. The source side can read only finite window data, so the first visible dependency is the $\StreamNameUp$ row named by the sibling source chapter.

The window data are then interpreted through $\RegSeqRatUp$ and bounded by the $\DyadicRatCoreUp$ tolerance ledger. These rows supply the finite regular-name and dyadic-readback surface used by separability consumers.

The terminal read is the $\RealUp$ seal. Since the route has no coordinate for quotient real equality, ambient completeness, or a choice-selected dense sequence, the L10 source chain is exhausted by the four displayed sibling chapters.
\end{proof}

\begin{theorem}[RealSeparability countable-dense Cauchy handshake]
\label{thm:real-separability-countable-dense-cauchy-handshake}
Every $\CountableDenseSubsetUp$ consumer of an accepted $\RealSeparabilityUp$ packet must first display finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance control, and the terminal $\RealUp$ seal, and only then read rational density. The handshake routes the dense subset surface of \autoref{ch:concrete-instances-countable-dense-subset-namecert} through the L10 source chain of \autoref{thm:real-separability-l10-source-route}; it exports no selected dense sequence, quotient stream equality, ambient completeness, or host enumeration of completed reals.
\end{theorem}
\begin{proof}
Project the accepted $\RealSeparabilityUp$ carrier and apply \autoref{thm:real-separability-l10-source-route}. The source route already forces finite $\StreamNameUp$ windows to be visible before any density read is consumed.

The windows are then read back by $\RegSeqRatUp$ and bounded by the $\DyadicRatCoreUp$ tolerance ledger. These rows supply the finite Cauchy-facing data needed by the countable dense subset consumer.

Only after the terminal $\RealUp$ seal is displayed may the consumer read rational density from \autoref{ch:concrete-instances-countable-dense-subset-namecert}. Since no selected dense sequence, quotient stream equality, ambient completeness, or host enumeration row appears in the displayed route, none can be exported by the handshake.
\end{proof}
