\begin{theorem}[RealSeparability hub sibling route]
\label{thm:real-separability-hub-sibling-route}
Every $\RealSeparabilityUp$ density read exported by \autoref{ch:concrete-instances-real-separability-namecert} factors first through the regular rational schedule of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. Only after those sibling rows are displayed may the packet expose a countable dense surface to a downstream consumer.
\end{theorem}
\begin{proof}
Read the existing RealSeparability carrier and sibling-lattice files through the hub. The regular rational schedule gives the rational approximants, the dyadic core gives the tolerance rows, and the stream-name route gives the finite observation windows that the density read may inspect.

The terminal $\RealUp$ seal is then read before the density surface is exported. Thus the hub route records a concrete L10 dependency through RegSeqRatUp, DyadicRatCoreUp, StreamNameUp, and RealUp rather than a detached dense subset, selected representative, quotient real equality, countable-choice selector, or ambient completeness row.
\end{proof}

\begin{theorem}[RealSeparability countable-dense forward read]
\label{thm:real-separability-countable-dense-forward-read}
Every $\CountableDenseSubsetUp$ or $\RealCauchyModulusUp$ consumer reading $\RealSeparabilityUp$ must pass through the sibling route named in \autoref{thm:real-separability-hub-sibling-route}, then through the countable-dense source of \autoref{ch:concrete-instances-countable-dense-subset-namecert} before exporting density. The route exports no selected dense point, quotient real equality, countable-choice selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:real-separability-hub-sibling-route}. It places every density read behind the RegSeqRat, DyadicRatCore, StreamName, and RealUp sibling rows before the hub exports a countable dense surface.

Project the carrier rows of \autoref{def:real-separability-carrier}. The rational enumeration, dyadic tolerance, finite window, regular readback, terminal Real seal, exactness, transport, replay, provenance, and local naming rows are the only data available to the separability consumer.

The countable-dense source of \autoref{ch:concrete-instances-countable-dense-subset-namecert} is therefore read after those sibling rows and before density is exported to either a $\CountableDenseSubsetUp$ or $\RealCauchyModulusUp$ consumer. Since the carrier contains no selected dense point, quotient real equality, countable-choice selector, or ambient completeness row, the forward read cannot export any of them.
\end{proof}
