\begin{theorem}[Real separability dyadic lattice link]
\label{thm:real-separability-dyadic-lattice-link}
Every $\RealSeparabilityUp$ density read consumes the dyadic density lattice through \autoref{ch:concrete-instances-real-namecert}, \autoref{ch:concrete-instances-rat-namecert}, and \autoref{ch:concrete-instances-dyadicratcore-namecert} before any separability observation is exported. The $\RealUp$ row supplies the terminal real-name seal, the $\RatUp$ row supplies the rational dense source, and the $\DyadicRatCoreUp$ row supplies the finite tolerance lattice that controls each displayed approximation window.

The same dependency route reads dense dyadic witnesses through \autoref{ch:concrete-instances-dyadicratcore-namecert}, regular-sequence readback through \autoref{ch:concrete-instances-regseqrat-namecert}, and the completed real seal through \autoref{ch:concrete-instances-real-namecert} before the $\RealSeparabilityUp$ carrier exports its finite density row.
\end{theorem}
\begin{proof}
Project the accepted separability packet to its displayed density route. A consumer first reads the real-name seal so that the observation is a $\RealUp$-facing read rather than a host dense-subset claim.

The rational source is then supplied by the $\RatUp$ row. Its enumeration is meaningful for separability only after the dyadic tolerance lattice has fixed the finite scale at which the approximation is inspected.

The $\DyadicRatCoreUp$ row supplies that finite scale and feeds the same request into the existing density route. Hence the separability observation cannot float as a kernel-only island: it is exported only after the real, rational, and dyadic lattice rows have all been consumed.
\end{proof}
