The dense-embedding route is the completion-facing dependency between the density siblings and the public separability row. A $\RealSeparabilityUp$ density consumer first reads the dyadic and rational density routes of \autoref{thm:real-separability-dyadic-rational-density-handoff} and \autoref{thm:real-separability-finite-density-exhaustion}; when the same consumer asks for completion-facing reuse, the finite dense image-window and approximation ledger of \autoref{ch:concrete-instances-dense-embedding-namecert} are read before the $\CountableDenseSubsetUp$ row is exported.

\begin{theorem}[Real separability dense-embedding route]\label{thm:real-separability-dense-embedding-route}
Every completion-facing $\RealSeparabilityUp$ density read that consumes canonical $\DenseEmbeddingUp$ data factors through the displayed dense image-window and approximation ledger before it reaches the $\CountableDenseSubsetUp$ boundary. Thus the separability packet may reuse dense-embedding data only as finite source, window, tolerance, approximation, and handoff rows, not as host topological density, a selected dense point, quotient real equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the finite density exhaustion of \autoref{thm:real-separability-finite-density-exhaustion}. The RealSeparability consumer already passes through $\RatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and the $\CountableDenseSubsetUp$ boundary.

Now insert the canonical dense-embedding packet of \autoref{ch:concrete-instances-dense-embedding-namecert}. Its completion handoff exposes only the dense image-window, approximation ledger, and local handoff rows before a completion-facing read is available.

Composing the two routes leaves the CountableDenseSubset row downstream of finite density data and finite dense-embedding data. Since neither route carries host topological density, selected dense points, quotient real equality, countable choice, or ambient completeness, the composed separability read exports none of those objects.
\end{proof}
