The $\RealSeparabilityUp$ packet supplies countable dense readback to the $\BishopCompleteMetricUp$ completion surface of \autoref{ch:concrete-instances-bishop-complete-metric-namecert}. A Bishop-complete-metric consumer first reads the separability carrier's dyadic density windows, $\StreamNameUp$ observations, $\RegSeqRatUp$ readback, and terminal $\RealUp$ seal, then passes those finite rows to the complete-metric route already mediated by the existing Real separability completion links.

\begin{theorem}[Real separability to BishopCompleteMetric forward link]
\label{thm:real-separability-bishop-complete-metric-forward-link}
Every $\BishopCompleteMetricUp$ consumer of an accepted $\RealSeparabilityUp$ packet factors through the displayed countable dense readback rows of \autoref{def:real-separability-carrier} before it may read the complete-metric surface of \autoref{ch:concrete-instances-bishop-complete-metric-namecert}. The handoff exports finite density windows, dyadic tolerances, regular rational readback, Real sealing, transport, replay, provenance, and local naming; it exports no selected dense point, quotient real equality, host completion object, countable-choice selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the Real separability carrier. Its dense-readback rows expose the rational enumeration, dyadic tolerance, StreamName window, regular rational readback, terminal Real seal, exactness ledger, transport, replay, provenance, and local naming.

Use the existing Real separability routes to metric completion and Cauchy-filter completion. Those child routes already force completion-facing reads through finite dyadic windows, regular readback, and the Real seal.

Now pass to \autoref{ch:concrete-instances-bishop-complete-metric-namecert}. The Bishop-complete-metric packet consumes metric-completion, Cauchy-filter, regular readback, separated metric, complete-metric, and Real-seal rows, so Real separability can feed it only through the displayed countable dense readback surface.

Since neither packet contains selected dense points, quotient real equality, host completion objects, countable-choice selectors, or ambient-completeness coordinates, the link is exactly the finite forward handoff stated above.
\end{proof}
