\begin{theorem}[Real separability Cauchy locator forward link]
\label{thm:real-separability-cauchy-locator-forward-link}
Every $\RealSeparabilityUp$ density read that feeds the locator surface of \autoref{ch:concrete-instances-cauchy-real-locator-namecert} passes through the displayed route
$$
\DyadicRatCoreUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp \longmapsto \CauchyRealLocatorUp .
$$
Concretely, the dyadic tolerance row is read before the finite StreamName window, the regular rational readback is read before the terminal Real seal, and the Cauchy locator receives only this finite-window density route. The link exports no quotient stream equality, selected nearest dense point, countable-choice search, trichotomy branch, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with the density carrier of \autoref{def:real-separability-carrier}. Its rows $Q,D,W,R,E,T,H,C,P,N$ place every density request behind the rational enumeration, dyadic tolerance, finite window, regular readback, and Real seal.

Use the existing separability routes. The rational dense handoff, dyadic-rational density handoff, and Cauchy completion route keep the density witness inside the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows already named by the packet.

Finally pass to \autoref{ch:concrete-instances-cauchy-real-locator-namecert}. Its locator requests consume dyadic tolerances, finite windows, regular readbacks, and the terminal Real seal in that order. Therefore a RealSeparability density read can feed $\CauchyRealLocatorUp$ only through the displayed finite route, with no hidden selector, quotient equality, choice schedule, trichotomy, or ambient completeness coordinate.

The same forward link is a consumer-side input for \autoref{ch:concrete-instances-cauchy-located-apartness-namecert}: its apartness request first reads the $\CauchyRealLocatorUp$ row, so the density support supplied by $\RealSeparabilityUp$ remains attached to the finite locator route rather than becoming an independent search principle.
\end{proof}
