\chapter{The Legitimate-Claim Problem for Finite Closed Systems}
\label{ch:visions-legitimate-claim-audit}
\origin{human}

BEDC is often encountered through particular targets: a concrete
\NameCert{} construction, a MetaCIC audit map, a halting boundary, or the
Riemann Hypothesis as a constructive witness target.  The common problem
behind these examples is more general.  Given a finite closed system
$\mathcal C$ and a finite expression $E$, what may $\mathcal C$ honestly
claim about $E$ without importing unmarked supply?  The answer is not always
``proof'' and not always ``failure''.  The answer is an audited claim status:
theorem, condition, route, evidence, non-evidence, meta-claim, refusal,
$\mathsf{GAP}$, or socket.

\section{Finite expressions and closed claim substrates}
\label{sec:legitimate-claim-finite-expressions}

\begin{definition}[Finite communicable expression]
\label{def:legitimate-claim-finite-expression}
A \emph{finite communicable expression} is a finite inscription or program
fragment that can be exchanged, inspected, and audited.  Definitions,
theorems, proofs, conjectures, programs, algorithms, theories, physical
interpretations, observation reports, equivalences, proof routes, rule
towers, meta-theorems, counterexamples, and numerical evidence all count as
finite communicable expressions when their presented form is finite.  The
expression may quantify over an infinite extension; finiteness concerns the
inscribed artifact.
\end{definition}

\begin{definition}[Closed claim substrate]
\label{def:closed-claim-substrate}
A \emph{closed claim substrate} is a system $\mathcal C$ whose internal uses
must pass through records, generators, classifiers, continuations, ledgers,
packages, certificates, or audit gates.  If a dependency cannot be generated,
defined, proved, classified, certified, or ledgered through those structures,
then it may not enter as anonymous theorem content.  It must be exposed as a
named boundary request.
\end{definition}

\begin{principle}[Closedness as named externality]
\label{prin:closedness-as-named-externality}
For BEDC, closedness is an accounting invariant:
$$
\text{closed}
\quad = \quad
\text{all external dependencies have apophatic names}.
$$
The invariant does not say that no external pressure appears.  It says that
no external pressure may be consumed without a visible name, ledger, or
socket.
\end{principle}

\begin{definition}[Positive and apophatic names]
\label{def:positive-and-apophatic-names}
A \emph{positive name} names an internally generated or internally specified
object: a carrier, constructor family, operation, law, eliminator,
classifier, or certificate field.  An \emph{apophatic name} names an
external dependency position.  It makes the dependency referable, turns it
into an auditable unit, and marks the boundary at which internal digestion
stops; it does not convert the dependency into a theorem, object, witness,
quotient representative, proposition equality, or causal law.
\end{definition}

\begin{definition}[Gap, socket, and far end]
\label{def:claim-gap-socket-far-end}
For a closed claim substrate $\mathcal C$, a request $\mathrm{req}$ forms
$\mathsf{GAP}_{\mathcal C}(\mathrm{req})$ when it asks for content not
produced by the displayed substrate.  If that gap is named as a typed or
ledgered boundary position, it forms
$\mathrm{socket}_{\mathcal C}(\mathrm{req})$.  For a forward-binding socket
$s$, its far end has only the apophatic reading
$$
\mathrm{FarEnd}(s) \equiv_{\mathrm{apo}} \mathsf{T}.
$$
The symbol $\mathsf{T}$ is not a proof source, state, rule, value, or global
oracle.  It is the common far-end name for uninternalized supply.
\end{definition}

\section{Claim status}
\label{sec:legitimate-claim-status}

\begin{definition}[Claim status]
\label{def:claim-status}
For a closed claim substrate $\mathcal C$ and a finite communicable
expression $E$, $\mathsf{ClaimStatus}_{\mathcal C}(E)$ is the audited status
that $\mathcal C$ may assign to $E$.  The principal statuses are:
\begin{description}
\item[Theorem row.] $E$ has a closed proof in the substrate.
\item[Conditional row.] $E$ is closed relative to displayed hypotheses,
  setup fields, or witness obligations.
\item[Route row.] $E$ supplies transports, equivalences, or a proof-search
  route without the witness needed to close the target.
\item[Evidence row.] $E$ supplies a trace, report, numerical datum, or metric
  indication that is admissible as evidence but not as theorem content.
\item[Non-evidence row.] $E$ supplies a report that is explicitly barred from
  serving as proof evidence.
\item[Meta row.] $E$ is a claim about a fragment, system, proof surface, or
  audit layer rather than a kernel-level theorem of the object language.
\item[Refusal row.] $E$ attempts to consume hidden supply and is rejected as
  an internal claim.
\item[$\mathsf{GAP}$ row.] $E$ exposes requested content not produced by the
  displayed substrate.
\item[Socket row.] $E$ names the boundary position at which such requested
  content would have to enter.
\end{description}
\end{definition}

\begin{definition}[Claim compiler]
\label{def:claim-compiler}
The \emph{claim compiler} of a closed substrate is the audit operation
$$
\mathsf{Compile}_{\mathcal C}
  : \mathsf{FiniteExpr}
  \longrightarrow
  \mathsf{ClaimStatus}_{\mathcal C}.
$$
Its inputs may be proof traces, programs, definitions, observations,
theories, routes, equivalence chains, or meta-claims.  Its outputs are
claim-status rows.  The compiler is therefore not merely a theorem machine;
it is a proof auditor, boundary detector, and refusal surface.
\end{definition}

\begin{theorem}[Claim-status exhaustion]
\label{thm:claim-status-exhaustion}
Let $\mathcal C$ be a closed claim substrate and let $E$ be a finite
communicable expression encoded for audit.  Then every accepted reading of
$E$ falls into one of the claim-status rows of \autoref{def:claim-status}.
If $E$ requests supply not generated by $\mathcal C$, then $E$ cannot be read
as an unconditional theorem row unless that supply is first discharged.
\end{theorem}

\begin{proof}
Inspect the dependencies of the encoded expression.  If they are all
generated, defined, proved, classified, certified, or ledgered through
$\mathcal C$, then the expression lands on the internal side: theorem,
condition, evidence, non-evidence, route, or meta-row according to the
shape of the supplied data.  If some dependency is requested but not
produced, the closedness invariant prevents anonymous internal use.  The
request is therefore recorded as a $\mathsf{GAP}$; if the request is named
as a boundary position, it is recorded as a socket.  If the expression tries
to consume the missing supply as theorem content, the proper status is a
refusal row.  These alternatives exhaust the admissible audit readings.
\end{proof}

\begin{theorem}[No hidden supply]
\label{thm:legitimate-claim-no-hidden-supply}
In a closed claim substrate, ungenerated, uncertified, and unledgered supply
breaks closedness when consumed as theorem content.  The same supply
preserves closedness when exposed as a socket and not consumed as an
internal proof source.
\end{theorem}

\begin{proof}
Closedness requires that every internal use be generated, certified, or
ledgered, and that every external dependency have an apophatic name.  An
ungenerated supply consumed as theorem content is an anonymous external
dependency, so it violates the invariant.  If the supply is exposed as a
socket, the substrate does not claim to possess it internally.  It records
the requested shape and the non-internalization boundary.  The accounting
invariant is therefore preserved.
\end{proof}

\begin{corollary}[Naming prevents smuggling]
\label{cor:legitimate-claim-naming-prevents-smuggling}
Apophatic naming does not solve the requested problem by naming it.  It
prevents the requested supply from being smuggled into theorem content.
\end{corollary}

\begin{proof}
A socket gives the audit gate a stable target: the site, requested supply,
non-internalization marker, and relevant gate can be inspected.  No witness
or theorem is produced merely by naming the socket.
\end{proof}

\section{Dual audit bases}
\label{sec:legitimate-claim-dual-audit-bases}

\begin{definition}[MetaCIC audit base]
\label{def:claim-metacic-audit-base}
The $\mathsf{MetaCIC}$ audit base is the closed-CIC meta-theory surface.  It
audits typing surfaces, beta steps, closedness, substitution, consistency
assembly, subject reduction, normalisation, confluence, and decidable
checking.
\end{definition}

\begin{definition}[GroundCompiler audit base]
\label{def:claim-groundcompiler-audit-base}
The $\mathsf{GroundCompiler}$ audit base is the compiler-facing surface.  It
audits event flows, source channels, generated recognizers, certificate
gates, metric boundaries, cannot-claim rows, streaming discipline, and
hidden-input boundaries.
\end{definition}

\begin{principle}[Dual-base non-collapse]
\label{prin:claim-dual-base-non-collapse}
BEDC self-audit uses the composition of $\mathsf{GroundCompiler}$ and
$\mathsf{MetaCIC}$, not their collapse.  GroundCompiler acceptance does not
become a proof-theoretic theorem by itself, and MetaCIC local decidability
does not become a global compiler or route oracle.
\end{principle}

\begin{theorem}[Dual audit of claim status]
\label{thm:dual-audit-claim-status}
For claims that involve both compiled artifacts and proof-theoretic content,
the legitimate status must pass through both audit bases.  A pass on one
base cannot silently discharge a blocked edge on the other.
\end{theorem}

\begin{proof}
GroundCompiler rows certify how an artifact entered the displayed event,
source-channel, recognizer, and certificate-gate surface.  MetaCIC rows
certify how a proof-theoretic claim behaves with respect to typing,
reduction, substitution, and closedness.  These are different coordinates.
If a claim is missing a source-channel boundary, MetaCIC typing does not
provide it.  If a claim is missing subject-reduction transport, a compiler
recognition row does not provide it.  The two bases therefore cooperate
without substituting for each other.
\end{proof}

\section{Infinite claims and global deciders}
\label{sec:legitimate-claim-infinite-global}

\begin{definition}[Finite grounding of an infinite claim]
\label{def:claim-finite-grounding}
An infinite claim $A_{\infty}$ has finite grounding when it is presented by
a finite generator, recognizer, continuation system, classifier, or packet
family together with a \NameCert{}, totality witness, correctness witness,
and dependency ledger sufficient to generate the required instances or
witnesses.
\end{definition}

\begin{definition}[Grounding rank]
\label{def:claim-grounding-rank}
The grounding rank of a claim is $0$ when the claim itself has a finite
certificate.  The rank is $n+1$ when the claim is generated by a rule whose
rank is $n$.  If no finite rank is available, the rank is $\omega$.
\end{definition}

\begin{theorem}[Infinite-claim closure]
\label{thm:claim-infinite-claim-closure}
An infinite claim with finite grounding rank may be used as an auditable BEDC
claim.  An infinite claim of rank $\omega$ cannot be consumed as proof
resource; it becomes a $\mathsf{GAP}$ socket unless further finite grounding
is supplied.
\end{theorem}

\begin{proof}
Finite rank gives a finite top certificate.  Certified transports or
generation steps then unfold the finite tower down to the target claim.
Rank $\omega$ gives no finite top.  Treating the whole tower as a single
object only creates a further demand for a generator and certificate for
that tower.  Without those data, the demand is a gap; once named, it is a
socket whose far end is read apophatically as $\mathsf{T}$.
\end{proof}

\begin{definition}[Global closure decider]
\label{def:claim-global-closure-decider}
A global closure decider is a classifier $D_{\mathrm{all}}(A,R)$ deciding,
for every theorem target $A$ and proof route $R$, whether $R$ eventually
outputs a closed proof of $A$.
\end{definition}

\begin{theorem}[Global closure deciders are not legitimate claim content]
\label{thm:claim-no-global-closure-decider}
No global closure decider is a legitimate internal BEDC claim object.
\end{theorem}

\begin{proof}
If such a decider existed, then for any certificate-level continuation
system $\NameCert_P$ and history $h$, form a route that runs the
$\Cont_P$-chain from $h$ and outputs a fixed proof of a trivial target
exactly when that chain terminates.  The decider would determine whether
the route closes, and hence whether the $\Cont_P$-chain terminates.  This
is the halting predicate of
\autoref{ch:visions-halting-as-form-of-distinction-limit}, which closes the
open meta loop at the certificate stratum.  The reflection boundary of
\autoref{ch:visions-reflection-and-limits} forbids that closure as internal
claim content.
\end{proof}

\section{The legitimate-claim theorem}
\label{sec:legitimate-claim-theorem}

\begin{definition}[Legitimate-claim problem]
\label{def:legitimate-claim-problem}
The \emph{legitimate-claim problem} asks: given a closed claim substrate
$\mathcal C$ and a finite communicable expression $E$, what is the strongest
non-oracular status that $\mathcal C$ may assign to $E$?
\end{definition}

\begin{theorem}[Legitimate-claim theorem]
\label{thm:legitimate-claim-theorem}
BEDC solves the legitimate-claim problem for finite communicable
expressions relative to a closed claim substrate: it assigns the strongest
non-oracular claim status obtainable from the displayed generators,
classifiers, continuations, ledgers, packages, certificates, audit gates,
MetaCIC rows, GroundCompiler rows, gap reports, and sockets.
\end{theorem}

\begin{proof}
By \autoref{thm:claim-status-exhaustion}, every accepted reading of an
encoded finite expression lands in a claim-status row.  If all relevant
dependencies are internal, the strongest status is read from the displayed
proof, condition, route, evidence, non-evidence, or meta-row.  If a
dependency is not generated, \autoref{thm:legitimate-claim-no-hidden-supply}
prevents its anonymous consumption and forces a gap or socket reading.  If a
claim requires both compiler-facing and proof-theoretic support,
\autoref{thm:dual-audit-claim-status} prevents either audit base from
impersonating the other.  If a claim tries to use a global closure oracle,
\autoref{thm:claim-no-global-closure-decider} rejects it as open-meta-loop
closure.  Thus the assigned status is non-oracular and maximal relative to
the displayed data.
\end{proof}

\begin{corollary}[Universal audit interface]
\label{cor:legitimate-claim-universal-audit-interface}
BEDC is a universal audit interface, not universal truth possession.  It
does not assert that every true proposition is provable, every question is
decidable, every external object is internalizable, or every boundary problem
has a positive solution.  It asserts that each finite claim must expose its
status as theorem, condition, route, evidence, non-evidence, meta-claim,
refusal, $\mathsf{GAP}$, socket, or $\mathsf{T}$-boundary.
\end{corollary}

\begin{proof}
The legitimate-claim theorem assigns an audited status to the finite claim.
Some statuses are proofs; others are conditional, evidential, boundary, or
refusal statuses.  The theorem therefore gives an audit interface rather
than a total truth predicate.
\end{proof}

\section{RH and observer language as tests}
\label{sec:legitimate-claim-tests}

\begin{corollary}[Riemann Hypothesis as witness-target test]
\label{cor:legitimate-claim-rh-test}
The Riemann Hypothesis illustrates the legitimate-claim theorem at maximal
mathematical pressure.  In BEDC it is a fixed constructive $\Pi$-statement;
a proof requires the witness function of
\autoref{prop:rh-constructive-form}; a disproof requires an explicit
counterexample packet; independence requires a fragment-specific
meta-theorem; unclosed equivalence chains remain routes; infinite rule
towers without finite grounding become sockets; and global route deciders
are halting-style oracles.
\end{corollary}

\begin{proof}
This is exactly the RH boundary analysis of
\autoref{ch:visions-rh-route-halting-boundary}, read as an instance of
\autoref{thm:legitimate-claim-theorem}.
\end{proof}

\begin{corollary}[Observer language as claim-status reconstruction]
\label{cor:legitimate-claim-observer-language}
The same audit interface applies to observer, time, space, and universe
language.  Such vocabulary is not admitted as an anonymous background.  It
must be reconstructed as record accumulation, local inscription,
inter-history coherence, gap report, socket, or $\mathsf{T}$-boundary.
\end{corollary}

\begin{proof}
The apophatic far-end chapters identify closed observational systems,
forward-binding sockets, local inscription, and the common far-end name
$\mathsf{T}$.  A claim about observers, time, space, or universe therefore
enters BEDC through the same status surface: generated records when
available, coherence rows when displayed, and sockets when the requested
supply is not internalized.
\end{proof}

\begin{corollary}[Finite closed systems can speak without hidden supply]
\label{cor:legitimate-claim-honest-speech}
A finite closed system can speak about infinity, proof, programs,
observers, time, space, truth, self-reference, and externality without
turning unmarked external supply into theorem content.
\end{corollary}

\begin{proof}
The system speaks by assigning claim status rather than by pretending that
every claim is an internal theorem.  Infinite claims require finite
grounding, proof claims require proof data, program claims face the halting
boundary, observer claims face the inscription and socket boundary, and
externality is named apophatically.  Each case preserves the closedness
invariant.
\end{proof}
