\chapter{Theory Stability and the TasteGate Framework}
\label{ch:visions-theory-stability-taste-gate}
\origin{human}

The 280-plus concrete-instance chapters of \texttt{papers/bedc/parts/}
formalise objects whose mathematical-consensus credit was earned by the
mathematics community over decades or centuries: $\GroupUp$, $\HilbertUp$,
$\CurvatureUp$, $\GelfandDualityUp$, $\DiffGaloisUp$, and the rest. Each
chapter inherits this credit; the BEDC formalisation does not need to
re-test whether $\GroupUp$ is a `real theory', because the question was
settled outside the system.

A separate admission mode applies when codex itself proposes a chapter. An
AI-proposed chapter has no mathematical-consensus credit. It might be
combinatorial padding, a synonym of an existing chapter under another name, a
carrier that crosses the BEDC zero-axiom boundary, or a locally self-consistent
surface that breaks stability of the existing horizon when admitted. The taste
gate of this chapter records the discipline by which AI-proposed chapters earn
admission.

The discipline reuses the conservativity, no-hidden-input, round-trip,
and source-channel-separation theorems already established in the
ground compiler chapters
(\autoref{ch:ground-compiler-event-flow},
 \autoref{ch:ground-compiler-zeckendorf-safe-channel-encoding},
 \autoref{ch:ground-compiler-source-channel-layer-separation},
 \autoref{ch:ground-compiler-main-theorems-cannot-claims}). It elevates
those compiler-internal invariants into a chapter-level taste gate.

\section{Carrier display obligations}
\label{sec:taste-gate-four-obligations}

A candidate chapter $X$ earns admission to the AI-proposed track by first
committing to a concrete carrier display. The Lean class
\texttt{BHistCarrier X} supplies
$$
\mathsf{toEventFlow}:X\to\EventFlow,
\qquad
\mathsf{fromEventFlow}:\EventFlow\to\mathsf{Option}(X).
$$
The chapter-specific gate then asks for only the two obligations that genuinely
depend on $X$.

\begin{definition}[Conservativity obligation]
\label{def:taste-gate-conservativity}
Conservativity is not a field supplied by the chapter. It is the theorem that
every mark occurring in the display of an admitted token is one of the two BEDC
ground marks $\bzero$ or $\bone$, derived from GroundCompiler event-flow
conservativity.
\end{definition}

\begin{definition}[No-hidden-input obligation]
\label{def:taste-gate-no-hidden-input}
No-hidden-input is not a field supplied by the chapter. It is the theorem that
every token $x:X$ has a visible event-flow witness $e$ with
$$
\mathsf{fromEventFlow}(e)=\mathsf{some}(x),
$$
obtained by taking $e=\mathsf{toEventFlow}(x)$ and applying the round-trip
obligation.
\end{definition}

\begin{definition}[Round-trip obligation]
\label{def:taste-gate-round-trip}
The round-trip obligation for $X$ asserts
$$
\forall x:X,\quad
\mathsf{fromEventFlow}(\mathsf{toEventFlow}(x))=\mathsf{some}(x).
$$
Every admitted token must be the readback of its own displayed event flow.
\end{definition}

\begin{definition}[Layer-separation obligation]
\label{def:taste-gate-layer-separation}
The layer-separation obligation for $X$ asserts
$$
\forall x,y:X,\quad
x\neq y\Rightarrow
\mathsf{toEventFlow}(x)\neq \mathsf{toEventFlow}(y).
$$
Distinct carrier tokens therefore have distinct displayed event flows.
\end{definition}

\section{Lean interface}
\label{sec:taste-gate-lean-interface}

The Lean interface separates carrier data from gate data:

\begin{verbatim}
class BHistCarrier (X : Type) where
  toEventFlow : X -> EventFlow
  fromEventFlow : EventFlow -> Option X

class ChapterTasteGate (X : Type) [BHistCarrier X] where
  round_trip :
    forall x : X,
      BHistCarrier.fromEventFlow
        (BHistCarrier.toEventFlow x) = some x
  layer_separation :
    forall x y : X, x <> y ->
      BHistCarrier.toEventFlow x <>
        BHistCarrier.toEventFlow y
\end{verbatim}
\leandef{BEDC.Meta.TasteGate.BHistCarrier}
\leandef{BEDC.Meta.TasteGate.ChapterTasteGate}
\leanchecked{BEDC.Meta.TasteGate.ChapterTasteGate.conservativity}
\leanchecked{BEDC.Meta.TasteGate.ChapterTasteGate.no\_hidden\_input}

The reference instance witnesses that the ground compiler's own event-flow
carrier satisfies the gate by identity display and identity readback. The
conservativity and no-hidden-input readings are obtained from the derived
theorems above, not from chapter-filled fields.

\leanchecked{BEDC.Meta.TasteGate.groundCompilerSelfTasteGate}

\section{Field faithfulness and nontriviality}
\label{sec:taste-gate-field-faithful-nontrivial}

The current Lean surface also records two opt-in strengthening gates.
\texttt{FieldFaithful} requires a chapter to list its $\BHist$ fields and prove
that equal field lists determine equal carrier tokens. \texttt{Nontrivial}
requires a displayed pair of distinct inhabitants, excluding one-token carriers
whose layer-separation proof would be vacuous.

\leandef{BEDC.Meta.TasteGate.FieldFaithful}
\leandef{BEDC.Meta.TasteGate.Nontrivial}

These gates do not replace \texttt{ChapterTasteGate}. They refine it: the
chapter must first be displayable and readable, and may then expose additional
evidence that the display reflects every declared field and that the carrier is
not a vacuous singleton.

\section{Relationship to the NameCert obligations}
\label{sec:taste-gate-versus-namecert}

The \emph{naming-certificate} obligation set
(\autoref{ch:core-typed-naming-certificates}) records source, classifier,
pattern, ledger, and extension obligations within a single chapter. The
TasteGate obligations record stability across chapters and across the
ground compilation layer. The two are orthogonal:

\begin{itemize}
\item A chapter satisfying $\NameCert$ alone is internally consistent
      but not necessarily stable when admitted to the global horizon.
\item A chapter satisfying TasteGate alone has display/readback stability
      but is not yet a usable BEDC carrier.
\item Human-curated chapters supply $\NameCert$ and inherit TasteGate
      credit from mathematical consensus.
\item AI-proposed chapters must supply both $\NameCert$ and TasteGate.
\end{itemize}

The chapter does not retroactively impose TasteGate on the existing
human-curated horizon. The audit gate distinguishes the two tracks by a
single \texttt{\textbackslash origin\{human|ai\}} field on the
\texttt{closurestatus} block; absence defaults to \texttt{human} and
preserves backward compatibility.

\section{Cannot-claim registry}
\label{sec:taste-gate-cannot-claims}

The chapter does not claim a complete answer to the underlying
philosophical question of what makes a mathematical object `real';
it claims only a machine-checkable filter. The chapter does not claim
that any failure of the four obligations rules a candidate out as
mathematics in some absolute sense; it rules the candidate out of
\emph{this} BEDC horizon under the AI-proposed track. The chapter does
not claim that human-curated chapters whose four obligations have not
been mechanically checked are incorrect; it claims only that they
inherit consensus credit and need not be re-checked at admission time.
The chapter does not claim a semantic conservativity theorem for arbitrary
chapter $X$ relative to an arbitrary BEDC baseline. It claims the narrower
ground-display conservativity supplied by the GroundCompiler event-flow theorem
for the displayed event flows of any admitted carrier.

\concretizedIn{ch:concrete-instances-policy-namecert}{Policy packets realize the TasteGate discipline as finite BHist action-selection certificates with explicit ground-compiler witness rows.}
\concretizedIn{ch:concrete-instances-tastegateadmission-namecert}{TasteGateAdmission packets realize AI-origin chapter admission as finite BHist rows carrying ChapterTasteGate, ground-compiler witness, audit-gate, hsame, Cont, Pkg, GAP, and NameCert data.}
\concretizedIn{ch:concrete-instances-tastegatecompilerwitness-namecert}{TasteGate admission is realized as a finite compiler-witness NameCert packet tying ChapterTasteGate obligations to ground-compiler witness rows.}
\concretizedIn{ch:concrete-instances-tastegatestability-namecert}{TasteGate stability is realized as finite BHist NameCert packets over ground-compiler witness rows, admission ledger, non-hidden-input, round-trip, and layer-separation gates.}
\concretizedIn{ch:concrete-instances-finitereflectiontuple-namecert}{Finite reflection tuples realize TasteGate stability as displayed tuple, image, readback, componentwise NameCert transport, and reflection-request rows.}
\concretizedIn{ch:concrete-instances-tastegateaudittrace-namecert}{TasteGate audit traces are realized as finite BHist packets carrying the four obligation witnesses, audit replay, ground-compiler provenance, and non-escape ledger for AI-origin chapter admission.}
