\section{Standard bridge}
\label{sec:ideal-quotient-kernel-standard-bridge}

\begin{theorem}[Ideal public surface standard bridge]
\label{thm:ideal-public-surface-standard-bridge}
Let $R$ carry a $\RingUp$ certificate with carrier $C$, classifier $\sim_R$, addition $+_R$, additive inverse $-_R$, zero $0_R$, multiplication $\cdot_R$, and subtraction $x-_R y:=x+_R(-_R y)$. Assume the ambient $\RingUp$ certificate has a standard bridge to an ordinary ring surface. Then the public $\IdealUp$ surface interprets over that standard ring as the ordinary ideal-predicate surface and re-encodes through the BEDC rows: carried predicates, zero membership, additive closure, additive inverse closure, internal multiplication, two-sided ambient absorption, finite meet, sum, ring-map preimage, principal generated ideals, and the quotient-kernel export surface. The bridge exports no host quotient carrier, host quotient primitive, or classifier-changing host equality to BEDC.
\end{theorem}
\leanchecked{BEDC.Derived.IdealUp.IdealUp\_StdBridge}
\begin{proof}
Unpack the $\IdealUp$ carrier inventory of \autoref{def:ideal-carried-predicate-rows}. The ordinary surface reads the BEDC predicate as a carried subset of the standard ring supplied by the ambient $\RingUp$ bridge. Carrier support, zero membership, addition, additive inverse, internal multiplication, classifier transport, and left and right absorption are exactly the rows displayed in \autoref{sec:ideal-certificate}.

The finite-meet constructor is interpreted pointwise. Apply \autoref{thm:finite-ideal-intersection-closure}: every indexed ordinary ideal row is carried back to the finite BEDC family, and the carrier conjunct supplies the empty-spine case. The sum constructor is interpreted by the additive decomposition ledger of \autoref{thm:ideal-sum-closure}; its least-upper-bound surface is the ordinary inclusion property recorded in the same public BEDC rows.

The preimage constructor uses the ambient bridges on the source and target $\RingUp$ certificates. Apply \autoref{thm:ring-map-ideal-preimage-ideal-closure}: carrier preservation, classifier preservation, and operation preservation turn the standard inverse-image ideal into the BEDC source predicate. Principal generated ideals are supplied by \autoref{thm:ideal-principal-generated-full-ideal-closure}, whose generator ledger is again expressed only by carried endpoints, classifier transport, and ideal rows.

For the quotient-kernel part, unfold \autoref{def:ideal-quotient-kernel-source-package}. Its comparison data are precisely the two carrier witnesses $C(x)$ and $C(y)$ and membership of the displayed difference in the ideal predicate. Apply \autoref{thm:ideal-quotientring-export-surface}; the exported diagonal, endpoint-transport, additive-descent, negation-descent, and multiplication-descent rows are the quotient-free standard comparison boundary.

Thus each public constructor is interpreted through the ambient standard ring bridge and then repacked by the BEDC certificate rows already cited in this chapter. Since the quotient-kernel surface exports only carried endpoints, classifier transport, and difference-membership rows, no host quotient carrier or host quotient primitive enters the BEDC interface.
\end{proof}
\leanchecked{BEDC.Derived.IdealUp.IdealUp\_concrete\_to\_schema}

\closureat{IdealUp}{matureStr}[BEDC.Derived.IdealUp.IdealQuotientKernel\_export\_surface]
\begin{closurestatus}{\IdealUp}
  \constructivestory{An ideal is carried as a predicate on the histories of an ambient $\RingUp$ certificate, together with the rows saying that its members are ring-carried, contain zero, close under addition, additive inverse, internal multiplication, classifier transport, and multiplication by every carried ambient endpoint. The carrier accepts exactly predicates with those rows, while the quotient-kernel surface accepts pairs $x,y$ only when both endpoints are carried and the displayed difference $x-_R y$ lies in the ideal; sameness is transported by the ambient ring classifier rather than by forming a quotient carrier. The source is the ambient ring certificate plus the carried ideal predicate, the pattern records finite meet, sum by additive decomposition, ring-map preimage, principal generated ideals, and the quotient-kernel diagonal and descent rows, and the ledger keeps membership witnesses, decomposition witnesses, image-membership witnesses, and difference-membership rows visible. The name-certificate obligations are supplied by zero membership for inhabitation, ambient classifier reflexivity, symmetry, and transitivity for endpoint comparison, and the ideal classifier-transport row for closure of membership under classified replacement. A pair history $h$ lies in the signature gap of an $\IdealUp$ token $p$ when the source-domain accepts the ambient ring endpoints and ideal predicate, the signature relation pairs the pair with an answer quotient-kernel package and evidence ledger, and token introduction names that answer as $p$; unfolded, the endpoint difference is a displayed ideal member and all additive, negation, and multiplication descent rows are those encoded by $p$. The standard bridge reads the BEDC predicate as an ordinary ideal predicate over the standard ring supplied by the ambient $\RingUp$ bridge and reads it back through the same row inventory, while explicitly exporting no host quotient carrier. The chapter registers this carried-predicate and quotient-kernel construction under the name $\IdealUp$; ideals remain predicates with transport and absorption rows over existing ring histories, with no host quotient primitive or classifier-changing equality introduced.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature IdealUp boundary covers carried predicates, finite meet, sum, preimage, principal ideals, the quotient-kernel export surface, and the paper-level standard bridge of \autoref{thm:ideal-public-surface-standard-bridge}.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.IdealUp.IdealQuotientKernel\_export\_surface}
  \bridgestatus{bridgeChecked}
  \notclaimed{This chapter does not close host quotient carriers, full standard ideal theory, or host quotient primitives.}
  \upgradepath{No further upgrade -- chapter at top of formal axis.}
\end{closurestatus}
