\begin{theorem}[Normalization candidate socket fuel boundary]
\label{thm:normalization-candidate-socket-fuel-boundary}
Every $\NormalizationCandidateSocketUp$ consumer that asks for bounded normalization receives only the displayed finite socket rows: the candidate term window $M$, a fuel row $U$, a bounded trace row $T$, a closedness-preservation row $Q$, and the structural rows $H,C,P,N$ that transport and name that finite route. The trace row records that the fuel-indexed computation reaches the displayed bounded result within $U$ steps and that each recorded step preserves the closedness row $Q$. The socket does not export a strong-normalization certificate, a no-infinite-reduction theorem, an erased candidate projection, global confluence, quotient syntax equality, host evaluator soundness, or completed closed consistency from this bounded trace.
\end{theorem}
\begin{proof}
Project the socket carrier of \autoref{def:normalization-candidate-socket-carrier}. The closed typed term window is available as $M$, while candidate, closed-candidate, and candidate-set rows remain the only rows that can support any strong-normalization export.

For bounded normalization, insert the fuel row $U$ and bounded trace row $T$ between the term window and the replay rows. The trace is finite because each step is indexed by the displayed fuel ledger rather than by an unbounded reduction argument.

Closedness preservation is carried separately by $Q$. Each trace edge may be read only together with the source and target closedness rows named by $Q$, so the consumer receives a closed finite computation rather than a global normalization theorem.

Finally, $H,C,P,N$ transport, replay, package, and name exactly these displayed rows. Since no strong-normalization certificate is a coordinate of the bounded route, the socket boundary refuses any consumer that tries to read strong normalization from fuel alone.
\end{proof}

\begin{theorem}[Normalization candidate socket candidate-set fuel route]
\label{thm:normalization-candidate-socket-candidate-set-fuel-route}
If an accepted $\NormalizationCandidateSocketUp$ packet exposes the candidate-set row $E$ and bounded fuel row $U$, then every bounded normalization read factors through candidate evidence, the closedness-preservation trace, App and Pi adequacy rows, the bounded trace, and the structural rows $H,C,P,N$. The route uses the candidate-set readback row $E$, the App adequacy row $A$, the Pi adequacy row $B$, the bounded trace row $T$, the closedness-preservation row $Q$, and the fuel row $U$; it does not export global strong normalization or completed closed consistency.
\end{theorem}
\begin{proof}
Project the socket rows from \autoref{def:normalization-candidate-socket-carrier}. The candidate-set row $E$ supplies the candidate evidence available to the bounded read, while the adequacy rows $A$ and $B$ keep application and Pi cases attached to that evidence.

Use \autoref{thm:normalization-candidate-socket-fuel-boundary}. The bounded fuel row $U$ and trace row $T$ display the finite computation, and the closedness-preservation row $Q$ accompanies each recorded step.

The transport and replay rows preserve the order of the read. Thus $H,C,P,N$ can move and name only the route that has already passed through candidate evidence, adequacy rows, bounded fuel, bounded trace, and closedness preservation.

Since neither the candidate-set route nor the bounded-fuel boundary contains a coordinate for global strong normalization or completed closed consistency, those conclusions are not exported by the packet.
\end{proof}

\begin{theorem}[Normalization candidate socket fuel-boundary candidate gate]
\label{thm:normalization-candidate-socket-fuel-boundary-candidate-gate}
A fuel-indexed normalization read of an accepted $\NormalizationCandidateSocketUp$ packet may lower or inspect the finite fuel boundary only while at least one of the candidate rows $K,D,E$ remains visible. If $K,D,E$ are erased, the read is forced to the frontier refusal row $F$ and cannot export no-infinite-reduction, evidence-erased strong normalization, global confluence, quotient syntax equality, host evaluator soundness, or completed closed consistency.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:normalization-candidate-socket-carrier}. The strong-normalization and no-infinite-reduction exports are mediated by the candidate rows $K,D,E$, while the fuel row is only route data for bounded inspection.

Apply the boundary theorem \autoref{thm:normalization-candidate-socket-boundary}. It places normalization-facing reads downstream of visible candidate evidence rather than downstream of the closed term window alone.

Use candidate-erasure refusal, \autoref{thm:normalization-candidate-socket-candidate-erasure-refusal}. When $K,D,E$ are removed, the packet has no candidate evidence to support a no-infinite-reduction read, so the frontier refusal row $F$ is the only admissible boundary.

Thus fuel inspection can refine a displayed bounded trace but cannot replace reducibility-candidate evidence. The excluded strong-normalization, confluence, quotient, evaluator, and consistency conclusions require coordinates absent from the fuel boundary.
\end{proof}

\begin{theorem}[Normalization candidate socket candidate-set readback]
\label{thm:normalization-candidate-socket-candidate-set-readback}
If an accepted $\NormalizationCandidateSocketUp$ packet exposes the candidate-set row $E$, then closed typed strong-normalization and no-infinite-reduction reads factor through the finite route
$$
M,E,A,B,I,H,C,P,N .
$$
Bounded fuel rows may refine the displayed trace, but they cannot replace $E$ as the candidate-set readback row. The packet therefore refuses global normalization, erased candidate projection, unrestricted subject reduction, global confluence, quotient syntax equality, host evaluator soundness, and completed consistency.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:normalization-candidate-socket-carrier}. The closed typed term window $M$ is available to the socket, but \autoref{thm:normalization-candidate-socket-boundary} places strong-normalization and no-infinite-reduction exports downstream of candidate evidence.

Now specialize that boundary to the candidate-set row $E$. The application adequacy row $A$ and Pi adequacy row $B$ can refine the route through function and dependent-function cases, while $I$ records the no-infinite-reduction read downstream of the candidate-mediated strong-normalization projection.

Use \autoref{thm:normalization-candidate-socket-fuel-boundary} for bounded fuel traces. A fuel row may display a finite computation and preserve closedness along that trace, but it supplies no candidate-set membership, no candidate soundness, and no beta-closure data. It therefore cannot replace $E$.

Finally $H,C,P,N$ transport, replay, source, and name the candidate-set route. Since neither the base carrier nor the bounded-fuel extension contains rows for global normalization, erased candidate projection, unrestricted subject reduction, global confluence, quotient syntax equality, host evaluator soundness, or completed consistency, those reads remain refused.
\end{proof}
