\chapter{A Concrete Naming Certificate for $\NormalizationCandidateSocketUp$}
\label{ch:concrete-instances-normalization-candidate-socket-namecert}
\origin{ai}

The $\NormalizationCandidateSocketUp$ packet realizes the candidate-mediated normalization evidence of \autoref{ch:metacic-normalization-audit-map} as a finite socket object. It sits beside the critical-path packet of \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, the normalization frontier of \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, the confluence audit packet of \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, and the normal-form consistency seal of \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert}. The packet separates candidate rows from closed-candidate rows and candidate-set rows, records the Pi and App adequacy surfaces, and keeps no-infinite-reduction exports downstream of supplied candidate evidence. It is not an unconditional closed-term strong-normalization theorem.

\begin{definition}[Normalization candidate socket carrier]
\label{def:normalization-candidate-socket-carrier}
A $\NormalizationCandidateSocketUp$ carrier is a finite $\BHist$ packet
$$
S=(M,K,D,E,A,B,I,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the closed typed MetaCIC term window, exposing the empty-context term, type, and closedness checks available to the audit map.
\item $K$ is the reducibility candidate row, carrying the candidate predicate and its strong-normalization consequence.
\item $D$ is the closed-candidate row, carrying closedness together with candidate evidence.
\item $E$ is the candidate-set membership row, carrying membership, soundness, and beta-closure data.
\item $A$ is the application adequacy row, recording the function-side Pi evidence, argument candidate evidence, and application candidate handoff.
\item $B$ is the Pi adequacy row, recording Pi-candidate and neutral-normal evidence consumed by typed application routes.
\item $I$ is the no-infinite-reduction row, downstream of the candidate-mediated strong-normalization projection.
\item $F$ is the frontier row, retaining the refusal of any read that asks for closed-term strong normalization after deleting $K$, $D$, or $E$.
\item $H$ records componentwise $\hsame$ transport for the term window, candidate row, closed-candidate row, candidate-set row, App adequacy row, Pi adequacy row, no-infinite-reduction row, frontier row, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a normalization-candidate socket request through $M,K,D,E,A,B,I,F,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\NormalizationCandidateSocketUp$, \autoref{ch:metacic-normalization-audit-map}, \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\NormalizationCandidateSocketUp}$ row.
\end{enumerate}
The classifier compares accepted sockets only through $M,K,D,E,A,B,I,F,H,C,P,N$. It has no coordinate for global closed-term strong normalization, evidence-erased candidate projection, unrestricted subject reduction, global confluence, quotient syntax equality, host evaluator soundness, completed closed consistency, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Normalization candidate socket boundary]
\label{thm:normalization-candidate-socket-boundary}
For every accepted $\NormalizationCandidateSocketUp$ carrier
$$
S=(M,K,D,E,A,B,I,F,H,C,P,N),
$$
the local socket exports closed typed strong-normalization and no-infinite-reduction evidence only through at least one of the candidate rows $K,D,E$. Application adequacy $A$ and Pi adequacy $B$ are admissible only as route data for that same candidate-mediated socket. Any consumer missing the candidate row, the closed-candidate row, or the candidate-set row reaches $F$ and cannot export closed-term strong normalization from this packet.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:normalization-candidate-socket-carrier}. The closed term window $M$ is present, but the socket does not attach strong normalization directly to $M$.

The candidate rows are the gate. A read may use $K$ as reducibility candidate evidence, $D$ as closed-candidate evidence, or $E$ as candidate-set membership evidence. The strong-normalization export is downstream of one of these rows.

The adequacy rows refine the same gate. The application row $A$ and Pi row $B$ supply route data for function, argument, Pi, and neutral cases, but neither row replaces candidate evidence.

The no-infinite-reduction row $I$ is downstream of the candidate-mediated strong-normalization projection. If a consumer omits $K,D,E$ or asks to erase them, the frontier row $F$ records the refusal.

Transport, replay, provenance, and local naming preserve this row order through $H,C,P,N$. Because no global normalization, unrestricted subject-reduction, global confluence, quotient syntax equality, host evaluator soundness, or completed consistency row occurs in the carrier, the socket cannot export one.
\end{proof}

\begin{theorem}[Normalization candidate socket candidate-erasure refusal]
\label{thm:normalization-candidate-socket-candidate-erasure-refusal}
Let $S=(M,K,D,E,A,B,I,F,H,C,P,N)$ be an accepted $\NormalizationCandidateSocketUp$ carrier. Any consumer that keeps the closed typed term window $M$ but deletes all candidate evidence rows $K,D,E$ cannot export the no-infinite-reduction row $I$ from this packet. Such a consumer must reach the frontier refusal row $F$. The App adequacy row $A$ and Pi adequacy row $B$ remain route data for candidate-mediated reads; they are not substitutes for reducibility candidate, closed-candidate, or candidate-set evidence.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:normalization-candidate-socket-carrier}. The closed typed term window $M$ is a visible socket input, but the carrier does not attach no-infinite-reduction evidence directly to $M$.

Apply \autoref{thm:normalization-candidate-socket-boundary}. That boundary places closed typed strong-normalization and no-infinite-reduction exports downstream of at least one of $K,D,E$.

Now delete all three candidate evidence rows. With $K,D,E$ absent, the consumer has no displayed reducibility candidate, closed-candidate, or candidate-set membership route from which $I$ can be replayed.

The adequacy rows do not close the gap. App adequacy $A$ and Pi adequacy $B$ organize function, argument, Pi, and neutral routes once candidate evidence is present, but neither row supplies candidate evidence on its own. Therefore the only available response is the frontier row $F$, and the packet refuses the evidence-erased no-infinite-reduction export.
\end{proof}

\begin{theorem}[Normalization candidate socket MetaCIC diamond route]
\label{thm:normalization-candidate-socket-metacic-diamond-route}
Every diamond-residual consumer of an accepted $\NormalizationCandidateSocketUp$ carrier
$$
S=(M,K,D,E,A,B,I,F,H,C,P,N)
$$
must first read the candidate rows $K,D,E$, the adequacy rows $A,B$, the no-infinite-reduction row $I$, and the frontier row $F$ before citing \autoref{ch:concrete-instances-metacic-diamond-residual-budget-namecert}. The MetaCIC diamond residual budget may consume the socket only after those candidate-mediated rows are visible; it cannot read a closed typed term window $M$ as a premise-free normalization endpoint.
\end{theorem}
\begin{proof}
Project the socket carrier of \autoref{def:normalization-candidate-socket-carrier}. The rows relevant to a diamond-residual consumer are displayed as $K,D,E,A,B,I,F$ inside the same finite packet.

Use \autoref{thm:normalization-candidate-socket-boundary}. It places closed typed strong-normalization and no-infinite-reduction exports downstream of at least one candidate evidence row among $K,D,E$.

Use \autoref{thm:normalization-candidate-socket-candidate-erasure-refusal}. It shows that deleting $K,D,E$ while retaining $M$ forces the frontier refusal row $F$, so the diamond-residual consumer cannot treat the closed term window alone as normalization evidence.

The adequacy rows $A$ and $B$ remain route data for candidate-mediated App and Pi reads, and $I$ remains downstream of the same candidate evidence. Therefore the sibling route to \autoref{ch:concrete-instances-metacic-diamond-residual-budget-namecert} is available only after $K,D,E,A,B,I,F$ are visible in the socket.
\end{proof}

\falsifiablePrediction{Any consumer missing candidate, closed-candidate, or candidate-set rows in a $\NormalizationCandidateSocketUp$ packet cannot export closed-term strong normalization from that packet.}

\independenceWitness{metaciccriticalpath, metacicnormalizationfrontier, metacicconfluenceauditpacket, normalformconsistencyseal: $\NormalizationCandidateSocketUp$ is not bijective to any listed sibling because it jointly carries candidate, closed-candidate, candidate-set, App adequacy, Pi adequacy, no-infinite-reduction, frontier, transport, replay, provenance, and local naming rows.}

Lean $\mathsf{TasteGate}$ coverage for this packet must provide $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for the candidate row family, the closed-candidate row family, the candidate-set row family, and the socket classifier.

\closureat{NormalizationCandidateSocketUp}{seedStr}

\begin{closurestatus}{\NormalizationCandidateSocketUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:normalization-candidate-socket-carrier} and \autoref{thm:normalization-candidate-socket-boundary} seed the finite candidate-mediated normalization socket over candidate, closed-candidate, candidate-set, App adequacy, Pi adequacy, no-infinite-reduction, and frontier rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global closed-term strong normalization, evidence-erased candidate projection, unrestricted subject reduction, global confluence, quotient syntax equality, host evaluator soundness, completed closed consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, candidate gate exactness, App and Pi adequacy compatibility, no-infinite-reduction routing, frontier refusal, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming for BEDC.Derived.NormalizationCandidateSocketUp.}
  \constructivestory{A $\NormalizationCandidateSocketUp$ packet is generated from one closed typed MetaCIC term window, candidate evidence, closed-candidate evidence, candidate-set evidence, App adequacy, Pi adequacy, no-infinite-reduction, frontier refusal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
