\begin{theorem}[Real selected transport fit scoped boundary package]
\label{thm:real-selected-transport-fit-scoped-boundary-package}
For the selected-transport data of
\autoref{thm:real-selected-transport-fit-from-stream-classifier}, the carrier
obligation
\autoref{thm:real-selected-transport-fit-carrier-obligation}, classifier
obligation
\autoref{thm:real-selected-transport-fit-classifier-obligation}, and ledger
obligation
\autoref{thm:real-selected-transport-fit-ledger-obligation} together form the
scoped RealUp selected-transport fit package. Its source side is made of RealUp
streams, RatUp rational observations, StreamNameUp selected contexts,
$\mathsf{Cont}$ rows, pointwise $\hsame$ transport, selected e-one displays,
and appended-tail probes. Its carrier choices are the rational-observation
streams and selected endpoints. Its classifier choices are the
$\mathsf{RatHistoryClassifier}$ row together with the
$\mathsf{RealConstantHistoryClassifier}$ rows.

The package binds the stability obligations to pointwise $\hsame$ transport,
contextual continuation closure, selected e-one tail determinacy, and
positive-denominator transport. Its ledger is exactly the selected index,
prefix surplus, transport rows, continuation rows, e-one displays, and
appended-tail probes enumerated in
\autoref{thm:real-selected-transport-fit-ledger-obligation}. Its exactness
boundary is precisely the displayed carrier and classifier boundary supplied by
\autoref{thm:real-selected-transport-fit-carrier-obligation} and
\autoref{thm:real-selected-transport-fit-classifier-obligation}. The standard
bridge clause is the transported RegSeqRat selected endpoint normalization
already carried by the same selected-transport certificates.
\end{theorem}
\begin{proof}
Start from the four-package selected-transport certificate
\autoref{thm:real-selected-transport-fit-from-stream-classifier}. It fixes the
RealUp stream source, RatUp observation stream, StreamNameUp selected context,
pointwise $\hsame$ rows, contextual $\mathsf{Cont}$ rows, selected e-one
displays, and finite-prefix readback surface used by the scoped package.

Apply \autoref{thm:real-selected-transport-fit-certificate} and
\autoref{thm:real-selected-transport-fit-appended-tail-certificate}. The first
certificate supplies the displayed carrier and classifier readback data, while
the second supplies the appended-tail probes that keep the endpoint exclusions
inside the same selected ledger.

Apply \autoref{thm:real-selected-transport-synchronized-e1-endpoints} and
\autoref{thm:real-selected-transport-constant-real-classifier-package}. These
identify the synchronized selected e-one endpoints and the constant-real
classifier rows that turn the rational endpoint package into the stated RealUp
and Completion boundary.

Now project the three obligation theorems. The carrier obligation gives the
rational-observation streams, selected endpoints, unary and positive
denominator rows, and endpoint exclusions. The classifier obligation gives the
$\mathsf{RatHistoryClassifier}$ and
$\mathsf{RealConstantHistoryClassifier}$ rows. The ledger obligation states
that the selected index, prefix surplus, transport rows, continuation rows,
e-one displays, and appended-tail probes are exactly the consumed resources.

No object outside $\mathsf{Cont}$, $\hsame$, RatUp, StreamNameUp, and RealUp is
used in these projections. Therefore the three obligations bind the
selected-transport fit site as a scoped package, with exactness given by the
displayed carrier and classifier boundary and with the standard bridge supplied
by the transported RegSeqRat selected endpoint normalization.
\end{proof}
