\begin{theorem}[LieGroup group and manifold sibling route]
\label{thm:lie-group-manifold-group-sibling-route}
Every accepted $\LieGroupUp$ carrier reads the $\GroupUp$ multiplication, inverse, and unit rows of \autoref{ch:concrete-instances-group-namecert} together with the $\ManifoldUp$ chart, atlas, and transition rows of \autoref{ch:concrete-instances-manifold-namecert} before exporting the smooth-group $\NameCert_{\LieGroupUp}$ surface. The exported route packages group operations, manifold chart data, smooth multiplication and inverse readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming; it does not add a second group carrier, a second manifold carrier, or an ambient smooth object outside the sibling rows.

In particular, the smooth multiplication and inversion names are downstream labels: the carrier first consumes the $\GroupUp$ multiplication/inverse obligation row and the $\ManifoldUp$ chart-compatibility row, and only then records their smooth compatibility inside the local $\NameCert_{\LieGroupUp}$ route.
\end{theorem}
\begin{proof}
Project the accepted $\LieGroupUp$ carrier to its algebraic rows. The multiplication, inverse, and unit data are read as the $\GroupUp$ operation surface before the smoothness rows are exported.

Project the same carrier to its geometric rows. The chart domains, atlas compatibility, and transition data are read as the $\ManifoldUp$ surface before any smooth-group NameCert is formed.

The local $\NameCert_{\LieGroupUp}$ row then binds these two sibling routes with the displayed smooth multiplication and inverse readback, transport, replay, and provenance rows. Since the carrier has no independent ambient group or manifold coordinate, every exported smooth-group certificate factors through the cited $\GroupUp$ and $\ManifoldUp$ rows.
\end{proof}
