\begin{theorem}[ContinuationMonad root formal NameCert handoff]
\label{thm:continuation-monad-root-formal-namecert-handoff}
Every downstream formal target consuming $\ContinuationMonadUp$ receives the local $\NameCert$ row only through the finite packet

$$
A,B,C,f,g,u,H,K,L,N.
$$

The received readings are exactly the displayed $\BHist$ source histories, $\Cont$ unit and bind tails, $\hsame$ transports, $\Pkg$ provenance, $\CategoryUp$ hom-carrier row, $\mathsf{ContinuationMorphism}$ row, and local $\NameCert$ row. No quotient Kleisli arrow, host-function composition, ambient category completion, external monad evaluator, or unlisted continuation generator is exported.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_root\_formal\_namecert\_handoff}
\begin{proof}
First apply \autoref{thm:continuation-monad-root-source-coverage}. It forces root consumers to read the source histories $A,B,C$ and continuation tails $f,g,u$ through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface of the packet.

Next use \autoref{thm:continuation-monad-root-formal-route-saturation}. Downstream formal targets receive exactly $A,B,C,f,g,u,H,K,L,N$ through the formal route, together with the displayed Category hom-carrier and $\mathsf{ContinuationMorphism}$ readings.

Finally compose with \autoref{thm:continuation-monad-root-ledger-saturation-boundary}. The ledger boundary is the same finite packet and admits no extra entry for quotient Kleisli arrows, host-function composition, ambient category completion, external evaluators, or unlisted continuation generators. Hence the local $\NameCert$ row reaches downstream formal targets only through the named packet and not through an external monad schema.
\end{proof}

\begin{theorem}[Category ContinuationMonad hom-carrier route]
\label{thm:category-continuationmonad-hom-carrier-route}
Every downstream formal target reading a $\ContinuationMonadUp$ packet through
$A,B,C,f,g,u,H,K,L,N$ receives its $\CategoryUp$ hom-carrier exposure exactly
through the displayed $\mathsf{CategoryHomCarrier}$ and
$\mathsf{ContinuationMorphism}$ rows. The route is the finite continuation
packet route; it is not host function composition, a quotient Kleisli arrow,
an ambient category completion, or an external monad evaluator.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_category\_hom\_carrier\_route}
\begin{proof}
Start with \autoref{thm:continuation-monad-root-formal-namecert-handoff}. It
fixes the downstream formal handoff to the finite packet
$A,B,C,f,g,u,H,K,L,N$ and already names the Category hom-carrier and
$\mathsf{ContinuationMorphism}$ readings as packet rows.

Next apply
\autoref{thm:category-hom-carrier-continuation-morphism-tail-correspondence}.
The Category side reads a hom carrier exactly as unary endpoint rows together
with a continuation morphism whose displayed tail is the morphism history.
Thus the $\mathsf{CategoryHomCarrier}$ row consumed downstream is the
continuation-tail row of the same packet.

Finally use \autoref{thm:continuation-monad-root-source-coverage},
\autoref{thm:continuation-monad-root-formal-route-saturation}, and
\autoref{thm:continuation-monad-root-ledger-saturation-boundary}. These root
source and ledger saturation results leave no additional coordinate for host
composition, quotient Kleisli arrows, ambient category completion, external
evaluators, or unlisted continuation generators, so the Category hom-carrier
route is exactly the displayed continuation packet route.
\end{proof}

\begin{theorem}[ContinuationMonad Category hom readback correspondence]
\label{thm:continuation-monad-category-hom-readback-correspondence}
Any $\CategoryUp$ hom-carrier read consumed by the $\ContinuationMonadUp$ formal target is exactly the readback of the finite packet rows
$$
A,B,C,f,g,u,H,K,L,N.
$$
The correspondence is carried by the displayed $\mathsf{CategoryHomCarrier}$ and $\mathsf{ContinuationMorphism}$ rows of the packet. It cannot be replaced by quotient Kleisli arrows, host-function composition, ambient category completion, an external monad evaluator, or an unlisted continuation generator.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_category\_hom\_readback\_correspondence}
\begin{proof}
First apply \autoref{thm:continuation-monad-root-formal-namecert-handoff}. It fixes the formal target handoff to the finite packet $A,B,C,f,g,u,H,K,L,N$ and names the Category hom-carrier and $\mathsf{ContinuationMorphism}$ rows as part of that packet.

Next use \autoref{thm:category-continuationmonad-hom-carrier-route}. The Category hom-carrier exposure reaches the formal target only through the displayed $\mathsf{CategoryHomCarrier}$ and $\mathsf{ContinuationMorphism}$ readings, so the Category-side readback is already the continuation packet readback.

Finally compose with \autoref{thm:continuation-monad-formal-target-readback-exhaustion}. The formal target has no remaining coordinate for quotient Kleisli arrows, host-function composition, ambient category completion, external monad evaluators, or unlisted generators. Hence every consumed $\CategoryUp$ hom-carrier read corresponds exactly to the finite continuation packet rows.
\end{proof}

\begin{theorem}[ContinuationMonad formal target readback exhaustion]
\label{thm:continuation-monad-formal-target-readback-exhaustion}
Every downstream formal target consuming the $\ContinuationMonadUp$ packet through
$$
A,B,C,f,g,u,H,K,L,N
$$
must first read the root formal $\NameCert$ handoff and the $\CategoryUp$ hom-carrier route. Therefore the target receives only the displayed $\BHist$ source histories, $\Cont$ continuation tails, $\hsame$ transports, $\Pkg$ provenance, Category hom-carrier row, $\mathsf{ContinuationMorphism}$ row, and local $\NameCert$ row; it receives no quotient Kleisli arrow, host-function composition, ambient category completion, external monad evaluator, or unlisted continuation generator.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_formal\_target\_readback\_exhaustion}
\begin{proof}
Start with \autoref{thm:continuation-monad-root-formal-namecert-handoff}. It fixes the formal handoff to $A,B,C,f,g,u,H,K,L,N$ and excludes quotient Kleisli arrows, host composition, ambient category completion, external evaluators, and unlisted generators from the local $\NameCert$ route.

Next apply \autoref{thm:category-continuationmonad-hom-carrier-route}. The Category hom-carrier exposure is not an ambient category completion; it is the displayed $\mathsf{CategoryHomCarrier}$ and $\mathsf{ContinuationMorphism}$ reading of the same finite continuation packet.

Finally compose with \autoref{thm:continuation-monad-root-source-coverage}, \autoref{thm:continuation-monad-root-formal-route-saturation}, and \autoref{thm:continuation-monad-root-ledger-saturation-boundary}. These root source, route, and ledger boundaries exhaust the readback surface, so every formal target consumes the finite packet and no external monad semantics.
\end{proof}

\begin{theorem}[ContinuationMonad formal route target exhaustion]
\label{thm:continuation-monad-formal-route-target-exhaustion}
Any formal target that reads the displayed continuation packet
$$
A,B,C,f,g,u,H,K,L,N
$$
must factor through the root formal $\NameCert$ handoff, the $\CategoryUp$
hom-carrier route, and the formal-target readback exhaustion. Therefore the
target receives only the displayed $\BHist$ source histories, $\Cont$
continuation tails, $\hsame$ transports, $\Pkg$ provenance, Category
hom-carrier row, $\mathsf{ContinuationMorphism}$ row, and local $\NameCert$
row. It cannot obtain quotient Kleisli arrows, host-function composition,
ambient category completion, external monad evaluators, or unlisted
generators.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_formal\_route\_target\_exhaustion}
\begin{proof}
First apply
\autoref{thm:continuation-monad-root-formal-namecert-handoff}. It fixes the
formal route to the finite packet $A,B,C,f,g,u,H,K,L,N$ and excludes quotient
Kleisli arrows, host composition, ambient category completion, external
evaluators, and unlisted generators from the local $\NameCert$ handoff.

Next use \autoref{thm:category-continuationmonad-hom-carrier-route}. The
Category hom-carrier exposure is the displayed $\mathsf{CategoryHomCarrier}$
and $\mathsf{ContinuationMorphism}$ reading of the same continuation packet,
not an external category-completion route.

Finally compose with
\autoref{thm:continuation-monad-formal-target-readback-exhaustion}. The
formal target has already read the root handoff and the Category route, and
the readback theorem exhausts the remaining consumer surface. Hence every
formal consumer factors through those three routes and receives no unlisted
continuation or monad data.
\end{proof}

\begin{theorem}[ContinuationMonad root formal handoff downstream coverage]
\label{thm:continuation-monad-root-formal-handoff-downstream-coverage}
Every accepted local consumer of the $\ContinuationMonadUp$ root formal handoff is exhausted by the displayed finite route
$$
A,B,C,f,g,u,H,K,L,N.
$$
Its consumer-facing use factors through one of the already enumerated rows: the $\BHist$ source histories $A,B,C$, the $\Cont$ unit and bind tails $f,g,u$, the componentwise $\hsame$ transport row $H$, the formal route and ledger rows $K,L$, the $\Pkg$ provenance row, the $\CategoryUp$ hom-carrier row, the $\mathsf{ContinuationMorphism}$ row, or the local $\NameCert$ row $N$. No quotient Kleisli arrow, host-function composition, ambient category completion, external monad evaluator, or unlisted continuation generator becomes an accepted alternative of the BEDC packet.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_root\_formal\_handoff\_downstream\_coverage}
\begin{proof}
Start with \autoref{thm:continuation-monad-root-formal-namecert-handoff}. It fixes the local handoff to the finite packet $A,B,C,f,g,u,H,K,L,N$ and states that downstream formal targets receive the local $\NameCert$ row only through the displayed source-history, continuation-tail, transport, provenance, Category hom-carrier, $\mathsf{ContinuationMorphism}$, and naming rows. Thus an accepted local consumer has no entry point before the finite handoff packet is read.

Apply \autoref{thm:continuation-monad-formal-target-readback-exhaustion}. The readback theorem forces any downstream formal target consuming the packet to read the root formal $\NameCert$ handoff together with the $\CategoryUp$ hom-carrier route. It also identifies the remaining readback surface with exactly the displayed $\BHist$, $\Cont$, $\hsame$, $\Pkg$, Category hom-carrier, $\mathsf{ContinuationMorphism}$, and local $\NameCert$ rows.

The ledger and coverage coordinates are therefore the same finite list. The route rows $K,L$ account for the formal route and ledger boundary, while $H$ transports only the displayed components and $N$ names only that packet. Since the handoff theorem excludes the quotient, host-composition, ambient-completion, external-evaluator, and unlisted-generator alternatives from the local export, and the readback-exhaustion theorem leaves no further downstream coordinate after the handoff and Category route are read, every accepted local consumer is exhausted by the enumerated rows and every excluded alternative remains outside the BEDC packet.
\end{proof}
