\begin{theorem}[ContinuationMonad root source coverage]
\label{thm:continuation-monad-root-source-coverage}
For every accepted $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, every root consumer must read the displayed source histories $A,B,C$ and the displayed continuation tails $f,g,u$ before any unit or bind law can be consumed. The source coverage is exactly the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface of $Z$; it does not pass through host functions, quotient Kleisli arrows, ambient hom sets, or unlisted generators.
\end{theorem}
\begin{proof}
Start with \autoref{thm:continuation-monad-root-route-source-exposure}. It identifies the source of a root read with $A,B,C,f,g,u,H,K,L,N$ and leaves no coordinate for an external source object.

Next use \autoref{thm:continuation-monad-root-continuation-rule-coverage}. Unit and bind reads are covered only after the displayed histories, tails, route row, transport row, ledger row, and local name have been read.

Finally apply \autoref{thm:continuation-monad-root-downstream-consumer-separation}. This excludes host functions, quotient Kleisli arrows, ambient hom sets, independent category carriers, and unlisted continuation generators from the root source route, so coverage is exactly the displayed packet.
\end{proof}

\begin{theorem}[ContinuationMonad root source triad exactness]
\label{thm:continuation-monad-root-source-triad-exactness}
For every accepted $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, every root consumer route is exactly the joint surface obtained from source exposure, continuation-rule coverage, and downstream consumer separation. The route consists of the displayed source histories $A,B,C$, continuation tails $f,g,u$, route row, transport row, ledger row, package provenance, and local naming row of $Z$; it contains no host function, quotient Kleisli arrow, ambient hom set, or unlisted continuation generator.
\end{theorem}
\begin{proof}
Apply \autoref{thm:continuation-monad-root-route-source-exposure}. It identifies the root route source with the displayed packet $Z=(A,B,C,f,g,u,H,K,L,N)$ and supplies no external source coordinate.

Next use \autoref{thm:continuation-monad-root-continuation-rule-coverage}. The unit and bind laws are readable only through the displayed histories, tails, route row, transport row, ledger row, and local name.

Finally apply \autoref{thm:continuation-monad-root-downstream-consumer-separation}. Downstream consumers cannot receive host functions, quotient Kleisli arrows, ambient hom sets, or unlisted continuation generators, so the three component surfaces exhaust the root consumer route exactly.
\end{proof}

\begin{theorem}[ContinuationMonad root generator consumer lock]
\label{thm:continuation-monad-root-generator-consumer-lock}
For an accepted $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, every generator-facing root consumer is locked to the generator closure surface of \autoref{ch:concrete-instances-generatorclosure-namecert} and to the existing generator-boundary refusal of $Z$. A consumer may read only the displayed source histories, continuation tails, transport rows, route rows, ledger rows, package rows, and local name rows; it may not introduce host functions, quotient Kleisli arrows, ambient hom sets, or continuation generators not listed in the packet.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_root\_generator\_consumer\_lock}
\begin{proof}
Read the generator side through \autoref{thm:continuation-monad-generator-category-triad}. It routes the generator face of $Z$ through \autoref{ch:concrete-instances-generatorclosure-namecert} and the same $A,B,C,f,g,u,H,K,L,N$ packet.

Then apply \autoref{thm:continuation-monad-generator-boundary-refusal}. The refusal row blocks every unit, bind, continuation rule, or route generator that is not already displayed in the accepted packet.

Combine this with \autoref{thm:continuation-monad-downstream-unblock-route-package}. Downstream consumers receive the generator-boundary refusal as part of the finite route package, so no host function, quotient Kleisli arrow, ambient hom set, or unlisted generator can be added at the consumer boundary.
\end{proof}

\begin{theorem}[ContinuationMonad root category generator obligation surface]
\label{thm:continuation-monad-root-category-generator-obligation-surface}
For every accepted $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, the root category-generator obligation surface is the shared finite package read through \autoref{ch:concrete-instances-category-namecert}, \autoref{thm:continuation-monad-generator-category-triad}, \autoref{thm:continuation-monad-root-bind-schedule-exhaustion}, and \autoref{thm:continuation-monad-downstream-unblock-route-package}. The surface consists only of the displayed $\BHist$ source rows, $\Cont$ unit and bind tails, componentwise $\hsame$ transports, $\Pkg$ provenance, $\NameCert$ rows, generator-boundary refusal, and $\CategoryUp$ hom-carrier readings.
\end{theorem}
\leanvariant{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_root\_kleisli\_associativity\_surface}
\begin{proof}
First apply \autoref{thm:continuation-monad-generator-category-triad}. It binds the $\CategoryUp$ hom-carrier surface of \autoref{ch:concrete-instances-category-namecert} and the generator-boundary surface to the same accepted packet $Z$.

Next use \autoref{thm:continuation-monad-root-bind-schedule-exhaustion}. The root unit and bind schedules are exhausted by $u,f,g,H,K,L,N$, so category and generator consumers cannot replace the schedule by host composition or quotient Kleisli arrows.

Finally apply \autoref{thm:continuation-monad-downstream-unblock-route-package}. It packages the triad and schedule exhaustion for downstream use, with no coordinate for ambient hom sets, external category completion, host functions, or unlisted generators.
\end{proof}

\begin{theorem}[ContinuationMonad root NameCert ledger exactness]
\label{thm:continuation-monad-root-namecert-ledger-exactness}
For every accepted $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, every root consumer receives exactly the source histories $A,B,C$, continuation tails $f,g,u$, unit and bind rows, generator-boundary refusal, $\CategoryUp$ hom-carrier readings, componentwise $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows assembled by \autoref{thm:continuation-monad-root-source-coverage}, \autoref{thm:continuation-monad-root-generator-consumer-lock}, and \autoref{thm:continuation-monad-root-category-generator-obligation-surface}. The same root consumer receives no host function, quotient Kleisli arrow, ambient hom set, or unlisted continuation generator.
\end{theorem}
\leanchecked{BEDC.Derived.ContinuationMonadUp.ContinuationMonadCarrier\_root\_namecert\_ledger\_exactness}
\begin{proof}
First apply \autoref{thm:continuation-monad-root-source-coverage}. It fixes the root source route to the displayed histories $A,B,C$, tails $f,g,u$, and the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface of $Z$.

Next apply \autoref{thm:continuation-monad-root-generator-consumer-lock}. It adds the generator-boundary refusal to the same accepted packet and blocks host functions, quotient Kleisli arrows, ambient hom sets, and unlisted continuation generators at every generator-facing root consumer.

Then apply \autoref{thm:continuation-monad-root-category-generator-obligation-surface}. It contributes the $\CategoryUp$ hom-carrier readings and confirms that the unit and bind schedules are read through the displayed continuation rows rather than through an external category or quotient Kleisli object.

The carrier coordinates are exhausted by $A,B,C,f,g,u,H,K,L,N$ together with the named source, continuation, generator, category, transport, route, provenance, and local naming readings supplied by these three theorems. No remaining coordinate can export a host function, quotient Kleisli arrow, ambient hom set, or unlisted continuation generator, so the root NameCert ledger is exact.
\end{proof}

\begin{theorem}[ContinuationMonad root source public contract]
\label{thm:continuation-monad-root-source-public-contract}
For every accepted root-source public consumer of $\ContinuationMonadUp$ packet $Z=(A,B,C,f,g,u,H,K,L,N)$, the public read factors through \autoref{thm:continuation-monad-root-source-coverage}, \autoref{thm:continuation-monad-root-generator-consumer-lock}, \autoref{thm:continuation-monad-root-category-generator-obligation-surface}, and \autoref{thm:continuation-monad-root-namecert-ledger-exactness} before any unit, bind, generator, or category surface is consumed. The resulting contract exposes only the displayed source histories, continuation tails, unit and bind rows, generator-boundary refusal, category-generator obligation surface, componentwise $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows of $Z$; it refuses host functions, quotient Kleisli arrows, ambient hom sets, and unlisted continuation generators.
\end{theorem}
\begin{proof}
First apply root source coverage. The public consumer must enter through the displayed histories $A,B,C$, continuation tails $f,g,u$, and finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $Z$.

Next apply the generator consumer lock. This makes the generator-facing route pass through the displayed generator-boundary refusal before any generator surface can be consumed.

Then apply the category-generator obligation surface. Category readings are available only through the named finite package and its $\CategoryUp$ hom-carrier readings, not through ambient hom sets or quotient Kleisli arrows.

Finally apply root NameCert ledger exactness. It assembles the four public readings into one ledgered route and leaves no coordinate for host functions, quotient Kleisli arrows, ambient hom sets, or unlisted continuation generators.
\end{proof}
