\chapter{A Concrete Naming Certificate for $\GeneratorClosureRobustnessUp$}
\label{ch:concrete-instances-generator-closure-robustness-namecert}
\origin{human}

The $\GeneratorClosureRobustnessUp$ packet records a finite hypercube and median-closure certificate for the zero-marker generator-closure robustness surface of \autoref{thm:philosophy-generator-closure-robustness}. It reads active median generators, median-essential codons, deletion-loss rows, $Q_{2}$ completion closure, and minimal percolating seeds as finite combinatorial data over $Q_{6}$. The chapter is a NameCert target for finite closure robustness only; it does not claim biological necessity, probabilistic selection, host-level optimality, or an unbounded search principle.

\begin{definition}[GeneratorClosureRobustness carrier]
\label{def:generator-closure-robustness-carrier}
A $\GeneratorClosureRobustnessUp$ carrier is a finite $\BHist$ packet
$$
G=(A,E,L,Q,P,T,H,C,K,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the active median-generator row, listing the two size-$7$ active generators and their common rigid skeleton.
\item $E$ is the median-essential row, listing the five codons whose deletion changes the median closure.
\item $L$ is the deletion-loss row, recording the finite lost-codon table for each median-essential deletion.
\item $Q$ is the $Q_{2}$ completion row, recording the rule that a three-of-four occupied $Q_{2}$ face adjoins the fourth vertex.
\item $P$ is the percolating-seed row, recording the $484$ size-$7$ $Q_{2}$-completion seeds and the absence of smaller percolating seeds.
\item $T$ is the trigger-closure row comparing rigid median generation with broad $Q_{2}$ percolation capacity.
\item $H$ is the componentwise $\hsame$ transport row for active-generator, deletion-loss, completion, seed, and trigger rows.
\item $C$ is the displayed $\Cont$ replay row forcing every robustness read through $A,E,L,Q,P,T,H$.
\item $K$ is the $\Pkg$ provenance over $\GeneratorClosureRobustnessUp$, finite codon-window rows, $Q_{6}$, $Q_{2}$ faces, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\GeneratorClosureRobustnessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only by this finite table data and its displayed transports.
\end{definition}

\begin{theorem}[GeneratorClosureRobustness NameCert obligations]
\label{thm:generator-closure-robustness-namecert-obligations}
For every accepted $\GeneratorClosureRobustnessUp$ carrier $G=(A,E,L,Q,P,T,H,C,K,N)$, the local $\NameCert_{\GeneratorClosureRobustnessUp}$ surface consists exactly of these rows:
\begin{enumerate}
\item carrier admission for the active median generators, median-essential list, deletion-loss table, $Q_{2}$ completion rule, percolating-seed table, trigger comparison, transport, replay, provenance, and local name;
\item active-generator exactness, requiring the two displayed size-$7$ generators and their common six-codon skeleton to be read before a rigidity claim is accepted;
\item deletion-loss exactness, requiring every median-essential deletion to expose its finite lost-codon row;
\item $Q_{2}$ completion exactness, requiring every completion step to be witnessed by a displayed axis-aligned $Q_{2}$ face with at least three current vertices;
\item seed minimality, requiring the no-size-$6$ row and the $484$ size-$7$ seed row before a percolation claim is accepted;
\item non-escape of biological necessity, probabilistic selection, unbounded search, host optimality, or hidden codon classifiers.
\end{enumerate}
No closure-robustness obligation is stored outside this finite packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:generator-closure-robustness-carrier}. The only rows available to the certificate are $A,E,L,Q,P,T,H,C,K,N$.

The active-generator and deletion-loss obligations read $A,E,L$ as finite tables. The median-generator claim is accepted only after the two size-$7$ generators and their common skeleton are displayed, and each essential deletion is accepted only with its listed lost-codon row.

The $Q_{2}$ completion and seed obligations read $Q$ and $P$. Each completion step is justified by a finite face row, and the percolation claim is accepted only after the no-smaller-seed row and the $484$ minimal-seed row are present.

The trigger and non-escape clauses follow through $T,H,C,K,N$. These rows package the finite comparison between rigid median generation and broad $Q_{2}$ percolation; they contain no biological-necessity coordinate, probability model, unbounded search oracle, host optimum, or hidden classifier.
\end{proof}

\begin{theorem}[GeneratorClosureRobustness trigger-closure boundary]
\label{thm:generator-closure-robustness-trigger-closure-boundary}
Every trigger-closure read of an accepted $\GeneratorClosureRobustnessUp$ packet factors through the displayed active-generator row, median-essential row, deletion-loss table, $Q_{2}$ completion rule, percolating-seed table, trigger comparison, componentwise transport, replay, provenance, and local NameCert row. A missing active-generator row, deletion-loss row, $Q_{2}$ face row, or minimal-seed row is a failure to land on the finite robustness surface, not a robustness counterexample.
\end{theorem}
\begin{proof}
Begin with an accepted trigger-closure read. Carrier admission exposes the rows $A,E,L,Q,P,T,H,C,K,N$ before the trigger comparison can be consumed.

If the read concerns median rigidity, it must inspect $A,E,L$: the active generators, essential codons, and deletion losses are the displayed finite evidence for the rigid skeleton.

If the read concerns completion percolation, it must inspect $Q$ and $P$: the $Q_{2}$ completion rule supplies the step witnesses, and the seed table supplies both the minimality lower bound and the $484$ size-$7$ witnesses.

The replay row $C$ and transport row $H$ keep these two closure surfaces in one packet. Therefore a route missing one of the listed finite rows has not reached the accepted trigger-closure boundary, while a route that reaches the boundary exports no hidden classifier, biological-necessity assertion, probabilistic model, host optimum, or unbounded search principle.
\end{proof}

\falsifiablePrediction{An accepted $\GeneratorClosureRobustnessUp$ read is refuted if a trigger-closure consumer reaches a rigidity or percolation conclusion without first displaying the active-generator row, deletion-loss table, $Q_{2}$ completion row, minimal-seed row, transport row, replay row, provenance row, and local naming row.}

\independenceWitness{active median generation, median-essential deletion, $Q_{2}$ completion, and minimal percolating seeds: none is bijective with $\GeneratorClosureRobustnessUp$ because the packet jointly carries the rigid median skeleton, deletion losses, percolation rule, seed count, trigger comparison, transport, replay, provenance, and local NameCert rows.}

\closureat{GeneratorClosureRobustnessUp}{seedStr}

\begin{closurestatus}{\GeneratorClosureRobustnessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:generator-closure-robustness-carrier}, \autoref{thm:generator-closure-robustness-namecert-obligations}, and \autoref{thm:generator-closure-robustness-trigger-closure-boundary} seed the finite generator-closure robustness carrier over active-generator, essential-codon, deletion-loss, $Q_{2}$ completion, seed, trigger, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, standard bridge checking, biological necessity, probabilistic selection, unbounded search, host optimality, or hidden codon classifiers.}
  \upgradepath{Obligation closure requires checked carrier admission, active-generator exactness, deletion-loss exactness, $Q_{2}$ completion exactness, seed minimality, trigger-closure boundary, and non-escape for BEDC.Derived.GeneratorClosureRobustnessUp.}
  \constructivestory{A $\GeneratorClosureRobustnessUp$ packet is generated from active median generators, median-essential deletion rows, deletion-loss tables, Q2 completion faces, minimal percolating seed rows, trigger comparison, componentwise transport, displayed replay, provenance, and a local NameCert row.}
\end{closurestatus}
