\origin{ai}

\subsection{A punctured codon cube at the code-read layer}
\label{sec:bioreality-h0-r-punctured-cube}

\paragraph{Claim and coordinate domain.}
This record concerns the claim \emph{h0.R.punctured.cube}: a six-bit codon coordinate chart may reveal a local tile with a punctured-cube profile inside the standard-code codon table. The carrier is the codon cube $Q_6$, where each codon is read as a three-letter word over a four-symbol alphabet and hence as one of $64$ vertices. The distinctions used here are the six-bit codon display, a local tile face, a singleton label corner, and a three-point label class. The only contact used for biological interpretation is a curated standard-code table assigning codons to amino-acid or stop labels. Consequently the result is a statement about codon-label readback, not about translation dynamics, folded structure, physical admissibility, function, mechanism, or biological universality.

\paragraph{Verified punctured set.}
The verified row identifies the set $R$ as the following $13$ codons:
$$
\begin{aligned}
R=\{&\mathrm{AAA},\mathrm{AGA},\mathrm{AGG},\mathrm{AUA},\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU},\\
&\mathrm{UAA},\mathrm{UAG},\mathrm{UCA},\mathrm{UGA},\mathrm{UUA}\}.
\end{aligned}
$$
The independent cardinality row gives $|R|=13$ and matches exactly the same codon list. The finite cell count attached to the tile is
$$
\begin{aligned}
f(R)=(13,16,4),
\end{aligned}
$$
so the recorded object has $13$ vertices, $16$ one-dimensional incidences, and $4$ two-dimensional faces in the local cubical representation. This is the finite reason for calling the pattern punctured-cube shaped: the object is not the whole codon cube, and it is not merely an unstructured list of labels; it carries a small face-incidence profile inside $Q_6$.

\paragraph{Label modules inside the punctured set.}
The module-classification row partitions the same $13$ codons without leftovers. The assigned modules are
$$
\begin{aligned}
\mathrm{agr}&=\{\mathrm{AGA},\mathrm{AGG}\},\\
\mathrm{ar\_lys}&=\{\mathrm{AAA}\},\\
\mathrm{cun}&=\{\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU}\},\\
\mathrm{ile\_met}&=\{\mathrm{AUA}\},\\
\mathrm{ssn}&=\{\mathrm{UCA},\mathrm{UUA}\},\\
\mathrm{stop\_trp}&=\{\mathrm{UAA},\mathrm{UAG},\mathrm{UGA}\}.
\end{aligned}
$$
The audit reports $R\_\mathrm{size}=13$, $\mathrm{assigned\_count}=13$, no missing codons from the modules, no extra module codons, and no unassigned codons. Thus the punctured-cube row is not only a geometric selection; it is also a complete finite decomposition of the selected codons into six named label modules.

\subsection{Spectral and sampling evidence}
\label{sec:bioreality-h0-r-punctured-cube-evidence}

\paragraph{Spectral row.}
The spectrum row records two distinguished rates and one radial parameter:
$$
\begin{aligned}
\lambda_M&=0.6752479308830213,\\
\lambda_R&=0.4758352843197002,\\
\mu&=3.051487585298128.
\end{aligned}
$$
The cubic relation is numerically satisfied to tolerance, with both the cubic-polynomial value and the radial-polynomial value reported as $-6.224354365258478\times 10^{-12}$. The spectral-radius entry equals $0.6752479308830213$, matching $\lambda_M$ in the row. These numbers do not supply a biological mechanism; they give a finite numerical signature of the local coordinate construction.

\paragraph{Shape significance against random samples.}
The shape-significance experiment used $N=2000$ sampled tables with seed $42$. It found $1$ exact shape match and $25$ matches at Jaccard threshold at least $0.9$. The resulting empirical rates are
$$
\begin{aligned}
p_{\mathrm{exact}}&=0.0005,\\
p_{\mathrm{Jaccard}\ge 0.9}&=0.0125.
\end{aligned}
$$
The sampling process required $57377$ distinct-sample attempts and recorded $55377$ duplicate retries. In the finite row, both $p\_\mathrm{value\_exact\_shape\_significant}$ and $p\_\mathrm{value\_high\_jaccard\_significant}$ are the same displayed values, respectively $0.0005$ and $0.0125$. This supports the claim that the observed local shape is sparse under the sampled comparison class, while still leaving the interpretation confined to the code-label layer.

\paragraph{Amino-acid-class-preserving null row.}
A separate null model preserving amino-acid classes also used $N=2000$ and seed $42$. It reports an observed $M$ size of $20$, exact-match count $0$, and lower-tail count $7$ for samples at or below the observed $M$ size. The recorded rates are
$$
\begin{aligned}
p_{\mathrm{aa\ class\ exact\ shape}}&=0.0,\\
p_{\mathrm{aa\ class\ lower\ tail}}&=0.0035.
\end{aligned}
$$
The row also records the corresponding significance values as $0.0$ and $0.0035$. Since no explicit codon list for $M$ is supplied in the finite row, this chapter uses only the verified scalar $\mathrm{observed\_M\_size}=20$ and does not invent an $M$ membership table.

\subsection{Prediction checks and scope control}
\label{sec:bioreality-h0-r-punctured-cube-prediction-scope}

\paragraph{Leave-one-code-out row.}
The leave-one-code-out check evaluated $23$ tables and $63$ total targets. Its baseline hit rate is $0.19821739130434785$. The row then records three stronger rates:
$$
\begin{aligned}
\mathrm{hit\_rate\_above\_baseline}&=0.9841269841269841,\\
\mathrm{hit\_rate\_in\_M\_minus\_T}&=0.9365079365079365,\\
\mathrm{hit\_rate\_in\_M\_minus\_T\_plus\_boundary}&=0.9841269841269841.
\end{aligned}
$$
These values indicate that the local coordinate construction has strong code-table recovery behavior in the tested leave-one-code setting. They do not show that the geometry causes translation or that it determines organism-level biology.

\paragraph{Family-resolved leave-one-code-out row.}
The family-resolved row reports $5$ families. The hit rates above baseline are
$$
\begin{aligned}
\mathrm{alternative\_yeast}&=0.8333333333333334,\\
\mathrm{bacterial\_plastid}&=1.0,\\
\mathrm{candidate\_other}&=1.0,\\
\mathrm{mitochondrial}&=1.0,\\
\mathrm{nuclear\_ciliate}&=1.0.
\end{aligned}
$$
This supplies a finite comparison across named code-table families. The weakest listed family rate is still above $0.8$, while four families are reported at $1.0$. The correct reading is that the local codon-tile statistic transfers well across these tested code-label rows; it is not a claim that all biological code variation is governed by this tile.

\paragraph{Leave-one-codon-out row.}
The leave-one-codon-out check records $\mathrm{anchor\_count}=0$, $\mathrm{boundary\_count}=5$, $\mathrm{closure\_coverage\_high}=8$, and $\mathrm{predictable\_count}=8$. Its recovery rate is
$$
\begin{aligned}
\mathrm{recovery\_rate}=1.0,
\end{aligned}
$$
and the row also records $\mathrm{recovery\_rate\_above\_threshold}=1.0$. This is consistent with the module row: every module has either predictable or boundary support, but that support is still a codon-label phenomenon. A recovered label is not a folded protein, a molecular mechanism, a physical feasibility proof, or a functional assay.

\paragraph{Local interpretation.}
The finite evidence supports the following local statement. In the standard-code label table, the $13$-codon set $R$ forms a punctured-cube shaped tile with $f$-vector $(13,16,4)$, complete module assignment, a recorded spectral signature, low empirical exact-shape frequency under the sampled nulls, and strong leave-one-out recovery behavior. The interpretation stops there. The curated table observes assignments from codons to amino-acid or stop labels; it does not observe ribosomal realization, kinetics, organismal context, tertiary structure, physical admissibility, biological function, or a universal law. Any claim crossing one of those boundaries requires a separate contact that measures that layer directly.

\subsection{Verdict for the finite row}
\label{sec:bioreality-h0-r-punctured-cube-verdict}

\paragraph{Accepted content.}
The claim is ready at the code-read layer. The accepted finite content is the explicit codon set $R$, the cardinality $13$, the punctured-cube incidence vector $(13,16,4)$, the six-module classification with no unassigned codons, the spectral values $\lambda_M=0.6752479308830213$, $\lambda_R=0.4758352843197002$, and $\mu=3.051487585298128$, the empirical shape rates $0.0005$ and $0.0125$, the amino-acid-class-preserving rates $0.0$ and $0.0035$, the leave-one-code rates $0.9841269841269841$ and $0.9365079365079365$, the family hit-rate table, and the leave-one-codon recovery rate $1.0$.

\paragraph{Rejected promotions.}
No result in this row licenses a statement about translation realization, folded structure, structural order, physical admissibility, biological function, mechanism, or universality. The contact is a standard-code label table, so the only biological readback available here is codon-to-label assignment. The local tile may be mathematically sharp and empirically sparse relative to the sampled null rows, but it remains a code-layer pattern until another experiment or curated observation supplies evidence at a higher layer.