\origin{ai}

\subsection{Family-stratified leave-one-code-out boundary test}
\label{subsec:h1-leave-one-code-out-by-family}

\paragraph{Claim being tested.}
This record concerns the claim identifier \texttt{h1.leave\_one\_code\_out.by\_family}.  The object under inspection is the standard-code codon table represented on the six-coordinate codon cube $Q_6$, with codons displayed as six-bit vertices and with curated amino-acid or stop labels attached as the biological readback layer.  The tested pattern is deliberately local: window-six coordinates may expose a boundary-tile organization around the codons whose labels vary across code tables, but the labels themselves enter through a curated standard-code table rather than through the coordinate geometry alone.  The biological layer claimed here is only \texttt{code\_read}.  The chapter therefore records a code-label phenomenon, not a claim about translation dynamics, folded structure, physical admissibility, biological function, mechanism, or universality.

\paragraph{Finite codon support.}
The finite exceptional set $R$ has cardinality $13$.  In the verified row \texttt{h0.R.cardinality.13}, the set is
$$
\begin{aligned}
R=\{&\mathrm{AAA},\mathrm{AGA},\mathrm{AGG},\mathrm{AUA},\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU},\\
&\mathrm{UAA},\mathrm{UAG},\mathrm{UCA},\mathrm{UGA},\mathrm{UUA}\}.
\end{aligned}
$$
The same list appears in the punctured-cube row \texttt{h0.R.punctured.cube}.  Its recorded face data are
$$
\begin{aligned}
f(R)=(13,16,4),
\end{aligned}
$$
so the row is not just a count: it also fixes the local cubical incidence pattern used by the boundary test.  This is the finite coordinate substrate on which the code-family comparison is performed.

\paragraph{Spectral and sampling context.}
The companion spectral row \texttt{h0.spectrum} records the numerical values
$$
\begin{aligned}
\lambda_M&=0.6752479308830213,\\
\lambda_R&=0.4758352843197002,\\
\mu&=3.051487585298128.
\end{aligned}
$$
The radial cubic residual is $-6.224354365258478\times 10^{-12}$, reported again as the cubic-polynomial residual, and the spectral-radius value in tolerance is $0.6752479308830213$.  These numbers do not turn the local tile into a biological mechanism; they only certify that the coordinate construction has a stable numerical signature in the finite calculation.

The shape-significance row \texttt{h0.M.shape.significance} used $N=2000$ sampled tables with seed $42$.  It required $57377$ distinct-sample attempts and encountered $55377$ duplicate retries.  Among those samples there was $1$ exact shape match and $25$ samples with Jaccard similarity at least $0.9$.  Thus
$$
\begin{aligned}
p_{\mathrm{exact}}&=0.0005,\\
p_{J\geq 0.9}&=0.0125.
\end{aligned}
$$
The amino-acid-class-preserving null row \texttt{h0.null.model.aa\_class\_preserving} also used $N=2000$ and seed $42$.  It records observed $|M|=20$, exact-match count $0$, and lower-tail count $7$, giving
$$
\begin{aligned}
p_{\mathrm{class\ exact}}&=0.0,\\
p_{\mathrm{class\ lower\ tail}}&=0.0035.
\end{aligned}
$$
These finite-row values support a non-random local code-table geometry under the tested null models.  They do not identify a causal biochemical origin.

\paragraph{Leave-one-code-out result.}
The global leave-one-code-out experiment \texttt{h1.leave.one.code.out} evaluated $23$ tables and $63$ targets.  Its baseline hit rate was $0.19821739130434785$.  The observed hit rate above that baseline was $0.9841269841269841$, the hit rate in $M\setminus T$ was $0.9365079365079365$, and the hit rate in $M\setminus T$ plus the boundary region was $0.9841269841269841$.  In symbols, the row records
$$
\begin{aligned}
\mathrm{baseline}&=0.19821739130434785,\\
\mathrm{above\ baseline}&=0.9841269841269841,\\
\mathrm{inside\ }M\setminus T&=0.9365079365079365,\\
\mathrm{inside\ }(M\setminus T)\cup\partial&=0.9841269841269841.
\end{aligned}
$$
This high recovery rate is the immediate background for the family-stratified row.  It says that the local boundary construction is a strong code-label predictor over the evaluated table differences, while still remaining a code-level predictor.

\paragraph{Family-stratified row.}
The primary row for this chapter is \texttt{h1.leave\_one\_code\_out.by\_family}, experiment run \texttt{7dda978c6c97}, verified at \texttt{2026-06-01T09:02:43+00:00}.  It partitions the evaluated code-table variation into $5$ families.  The family hit rates above baseline are
$$
\begin{aligned}
\mathrm{alternative\ yeast}&=0.8333333333333334,\\
\mathrm{bacterial\ plastid}&=1.0,\\
\mathrm{candidate\ other}&=1.0,\\
\mathrm{mitochondrial}&=1.0,\\
\mathrm{nuclear\ ciliate}&=1.0.
\end{aligned}
$$
Thus four of the five recorded families reach perfect above-baseline hit rate in this finite row, while the alternative-yeast family remains high at $5/6=0.8333333333333334$.  The row therefore sharpens the earlier aggregate result: the signal is not confined to a single code-table family, and the weaker family is still far above the aggregate baseline value $0.19821739130434785$.

\paragraph{Codon-module localization.}
The related module-classification row \texttt{h1.leave\_one\_codon\_out.module\_classification} assigns every codon in $R$ to one of six named modules.  The recorded modules are
$$
\begin{aligned}
\mathrm{AGR}&=\{\mathrm{AGA},\mathrm{AGG}\},\\
\mathrm{AR\_Lys}&=\{\mathrm{AAA}\},\\
\mathrm{CUN}&=\{\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU}\},\\
\mathrm{Ile\_Met}&=\{\mathrm{AUA}\},\\
\mathrm{SSN}&=\{\mathrm{UCA},\mathrm{UUA}\},\\
\mathrm{Stop\_Trp}&=\{\mathrm{UAA},\mathrm{UAG},\mathrm{UGA}\}.
\end{aligned}
$$
The classification completeness check records $R\_\mathrm{size}=13$, assigned count $13$, no extra module codons, no missing codons, and no unassigned codons.  Hence the family-stratified code-table result can be read against a complete local module cover of the punctured-cube set $R$.  The companion leave-one-codon-out row gives anchor count $0$, boundary count $5$, high closure coverage $8$, predictable count $8$, and recovery rate $1.0$.  The local picture is therefore boundary-heavy rather than anchor-driven.

\paragraph{Reality contact.}
The only biological contact used here is the curated standard-code table, recorded under \texttt{curated.standard.code.table}.  Its observed fact is that codons are assigned amino-acid or stop labels in a curated genetic-code table.  The resolution is codon label readback.  This contact can test the code-read layer and local codon-tile label splits, but it cannot test translation realization, structural order, physical admissibility, or function realization.  The contact is consequently sufficient for checking whether a coordinate tile correctly predicts label behavior, and insufficient for any statement about what ribosomes do, how proteins fold, which molecules are physically admissible, or which phenotypes are functional.

\paragraph{Scope limit.}
The boundary probe \texttt{codon.local.tile.no.global.law} requires the local codon-tile pattern to remain at the code-read layer unless a separate higher-layer contact is supplied.  The aligned mismatch row \texttt{codon.local.tile.scope.boundary} states that the curated table supports code-layer readback and blocks promotion to protein realization, folded structure, physical admissibility, biological function, and universal mechanism.  The blocked-null row \texttt{codon.label.readback.not.folded.structure} makes the same restriction sharper: amino-acid label readback is not a folded-structure observation.  A further blocked-null row rejects promotion from mixed or malformed probe-token wording, cross-organism CUN/UUR wording, or tRNA-Leu notation into structure, translation, function, physical admissibility, or a global biological law.

\paragraph{Verdict.}
The finite rows support the following bounded conclusion.  In the six-coordinate codon cube, the $13$-codon punctured-cube set $R$ has a recorded local incidence pattern, a stable spectral signature, significant deviation from the sampled null models, complete module classification, and strong leave-one-code-out recovery across $5$ code-table families.  The family row is especially strong: bacterial-plastid, candidate-other, mitochondrial, and nuclear-ciliate families each have hit rate $1.0$ above baseline, and alternative yeast has hit rate $0.8333333333333334$.  The result is ready as a finite code-read claim.  It remains deliberately silent about translation, folding, physical admissibility, function, mechanism, and universality, because the supplied contact is a code-label table rather than an experiment at those higher biological layers.