\subsection{Start--Stop Window Eligibility as a Bounded ORF Test}\label{subsec:h2-orf-start-stop-window-eligibility}
\origin{ai}

\paragraph{Object of the finite row.}
This row concerns only the eligibility of a nucleotide window under a start/stop codon enumeration rule.  The biological object is not a translated product, a protein fold, a kinetic mechanism, or a cellular function.  The row records a narrow classification problem: given an externally supplied nucleotide interval, decide whether its boundary pattern is accepted by the declared start/stop-window enumerator.  In the direct row for claim $\mathrm{h2.orf.start\_stop.window\_eligibility}$, the external window manifest was loaded with value $1$, the finite manifest contained exactly one input window, and the enumerator classified exactly that one window:
$$
\begin{aligned}
\mathrm{input\_windows} &= 1,\\
\mathrm{classified} &= 1,\\
\mathrm{window\_count} &= 1.
\end{aligned}
$$
The scope field is $\mathrm{external\_window\_start\_stop\_enumeration\_only}$, and the row explicitly records $\mathrm{no\_geometry\_to\_translation\_promotion}=\mathrm{orf\_eligibility\_only}$.  Thus the mathematical content is a finite boundary enumeration against an annotation input, not a derivation of expression, translation, folding, physical admissibility, function, mechanism, or universality.

\paragraph{Codon sets used as the finite coordinate background.}
The row is read against the previously verified finite codon background.  The motif-compressed set $R$ is exactly
$$
\begin{aligned}
R=\{&\mathrm{AAA},\mathrm{AGA},\mathrm{AGG},\mathrm{AUA},\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU},\\
&\mathrm{UAA},\mathrm{UAG},\mathrm{UCA},\mathrm{UGA},\mathrm{UUA}\}.
\end{aligned}
$$
The audit row reports no missing and no extra elements for this equality.  The larger set $M$ has cardinality $20$ and is exactly
$$
\begin{aligned}
M=\{&\mathrm{AAA},\mathrm{AAG},\mathrm{ACA},\mathrm{ACG},\mathrm{AGA},\mathrm{AGG},\mathrm{AUA},\mathrm{AUG},\\
&\mathrm{CUA},\mathrm{CUC},\mathrm{CUG},\mathrm{CUU},\mathrm{UAA},\mathrm{UAG},\mathrm{UCA},\mathrm{UCG},\\
&\mathrm{UGA},\mathrm{UGG},\mathrm{UUA},\mathrm{UUG}\}.
\end{aligned}
$$
The finite saturation check gives
$$
\begin{aligned}
\operatorname{Sat}_{f_3}(R)=\{&\mathrm{AAA},\mathrm{AAG},\mathrm{AGA},\mathrm{AGG},\mathrm{AUA},\mathrm{AUG},\mathrm{CUA},\mathrm{CUC},\\
&\mathrm{CUG},\mathrm{CUU},\mathrm{UAA},\mathrm{UAG},\mathrm{UCA},\mathrm{UCG},\mathrm{UGA},\mathrm{UGG},\\
&\mathrm{UUA},\mathrm{UUG}\},
\end{aligned}
$$
while $M$ is recovered as $\operatorname{Med}(R)\cup\{\mathrm{ACA},\mathrm{ACG}\}$ with the same twenty displayed elements.  The listed boundary for $f_3$ is empty.  These set equalities describe the finite codon-coordinate background in which the start/stop-window test is expressed; they do not by themselves establish that any organism translates the window.

\paragraph{Quotient geometry and its limited use.}
The quotient audit supplies a compact finite geometry for $M$.  The reported $f$-vector of $M$ is
$$
\begin{aligned}
(20,38,26,8,1),
\end{aligned}
$$
and the quotient has size $10$ with $f$-vector
$$
\begin{aligned}
(10,14,6,1).
\end{aligned}
$$
The quotient representatives are the ten binary rows
$$
\begin{aligned}
&(0,0,0,0,1),\ (0,0,0,1,1),\ (0,0,1,0,1),\ (0,0,1,1,1),\\
&(0,1,0,0,0),\ (0,1,0,0,1),\ (1,0,0,0,1),\ (1,0,1,1),\\
&(1,0,1,0,1),\ (1,0,1,1,1).
\end{aligned}
$$
The entry $ (1,0,1,1)$ is recorded exactly as a four-coordinate row in the supplied audit table, while the other displayed entries are five-coordinate rows.  This asymmetry is treated here as a finite-row transcription feature rather than repaired silently.  The quotient data may organize the codon background, but the biological assertion in this subsection still requires an interval supplied from outside the coordinate calculation.

\paragraph{Contact status of the seed row.}
The top-level contact list for this packet is empty, and the conjectural carrier, distinctions, and readback are marked as awaiting contact with biological data.  Consequently, the direct seed row is only a rule-bound preparation for a possible ORF-eligibility test.  It is admissible to say that a start/stop enumeration has classified the one supplied manifest window; it is not admissible to say, from that enumeration alone, that translation occurred or that a protein product exists.  The two probes attached to the row enforce exactly this boundary: the packet breaks if it asserts ORF eligibility without a sequence, transcript, or curated interval annotation that can test the interval, and it also breaks if it promotes the boundary pattern to translation, structure, physical admissibility, function, or mechanism.

\paragraph{Separate curated-interval contact.}
A linked finite contact row gives a stronger, but still bounded, result for curated intervals.  That row loaded $168$ records from a curated ORF interval contact dataset whose source is NCBI RefSeq GenBank XML CDS intervals for \textit{Escherichia coli} K--12 MG1655 accession $\mathrm{NC\_000913.3}$.  The protocol was frozen at $2026$-$05$-$29\mathrm{T}19{:}11{:}13+00{:}00$, and the external evidence was observed at $2026$-$05$-$30\mathrm{T}10{:}29{:}31+00{:}00$.  The classifier identifier was $\mathrm{orf\_start\_stop\_window\_eligibility}$, and the row states that classifier rules were not modified after freezing.

The curated contact separates three input classes: $\mathrm{positive\_curated\_orf}$, $\mathrm{matched\_non\_orf\_decoy}$, and $\mathrm{boundary\_case}$.  Among positives, all $72$ of $72$ were accepted, giving accept rate $1.0$ and one-sided binomial upper-tail value $2.117582368135751\times 10^{-22}$.  Among matched decoys, all $72$ of $72$ were rejected, giving reject rate $1.0$ with the same reported binomial value.  The predeclared paired comparison also recorded $72$ wins in $72$ pairs, win rate $1.0$, and the same one-sided binomial value:
$$
\begin{aligned}
P_{\mathrm{pos}} &= 2.117582368135751\times 10^{-22},\\
P_{\mathrm{decoy}} &= 2.117582368135751\times 10^{-22},\\
P_{\mathrm{pair}} &= 2.117582368135751\times 10^{-22}.
\end{aligned}
$$
The three held-out folds were $\mathrm{refseq\_nc\_000913\_left\_locus\_fold}$, $\mathrm{refseq\_nc\_000913\_middle\_locus\_fold}$, and $\mathrm{refseq\_nc\_000913\_right\_locus\_fold}$.  Each fold contained $24$ positives and $24$ decoys, each fold passed, each positive accept rate was $1.0$, and each decoy reject rate was $1.0$.  The $24$ boundary cases had promoted count $0$ and promoted fraction $0.0$.

\paragraph{Local verdict.}
The finite evidence supports a narrow statement: the declared start/stop-window classifier can classify the one supplied external-window manifest row, and a separate curated-interval contact reports perfect separation on its finite $168$-row dataset under the frozen protocol just described.  The statement does not extend beyond those inputs.  In particular, neither the codon sets $R$ and $M$, nor the quotient geometry of $M$, nor the curated-interval contact entails translation realization, protein folding, physical admissibility, biological function, molecular mechanism, or a universal law for all possible nucleotide windows.  Those stronger biological claims would require additional contacts whose measurements are appropriate to those layers.  The self-check row is consistent with this restriction: it reports a BioReality-only boundary with three checked gates and states that no codon geometry is promoted across biological layers.