\subsection{NameCert: h2.orf\_eligibility.curated\_interval\_contact}
\label{sec:namecert-h2_orf_eligibility_curated_interval_contact}
\origin{ai}
\noindent\textit{Proposed by bio-namer; review status: draft.}

\paragraph{NameCert chapter slug.}
Proposed slug: `14104\_reality\_bound\_codon\_topology\_orf\_interval\_contact\_namecert\_construction`. The concept is BioReality-namespaced through `RealityBoundCodonTopology` and an ORF-interval-contact ledger. It avoids Loning's occupied `Codon64`, `Q\_6`, `M\textasciicircum{}star`, `StopCodonZeckendorfSuffix`, support-nerve, trigger-lattice, and standard-code bridge-row names while preserving the intended Loning-format concrete NameCert shape.

\paragraph{Carrier.}
Carrier name: `RealityBoundCodonTopologyOrfIntervalContactLedger`. BEDC 5-tuple: `(carrier, distinctions, internal\_geometry\_packet, external\_reality\_bridge, cannot\_claim\_boundary)`. The carrier is a finite NameCert-facing ledger for the claim that a frozen start/stop-window geometry classifier made contact with an external curated ORF-interval dataset. The distinctions component records the experiment's declared row classes and classifier-output roles. The internal\_geometry\_packet records only BEDC-facing finite codon-window partition, median-closure, spectrum, and quotient context as geometry. The external\_reality\_bridge points to curated NCBI RefSeq and genetic-code sources, experiment-run provenance, and statistical witness records. The cannot\_claim\_boundary blocks translation realization, protein structure, physical admissibility, biological function, biological-code necessity, universal mechanism, and out-of-dataset classification.

\paragraph{Distinctions.}
- `positive\_curated\_orf`: externally curated ORF interval rows used only as curated biological reality contacts. - `matched\_non\_orf\_decoy`: matched decoy rows used as external controls against geometry-only overclassification. - `boundary\_case`: boundary rows used to verify that the classifier does not promote ambiguous or non-contact windows. - `orf\_start\_stop\_window\_eligibility`: the frozen classifier identifier, treated as a finite geometry-only rule packet. - `start\_codon\_hit`: a classifier-output distinction for a start event inside the supplied window. - `terminal\_stop\_hit`: a classifier-output distinction for a terminal stop event inside the supplied window. - `ambiguous\_base\_flag`: a separation marker preventing ambiguous windows from being promoted as interval contacts. - `heldout\_split`: the experiment's fold-level stability distinction, kept as provenance rather than BEDC kernel data. - `matched\_context\_id`: the positive/decoy pairing distinction for the predeclared paired baseline witness. - `external\_orf\_interval\_contact\_only`: the scope distinction separating curated biological interval contact from translation, folding, physical admissibility, function, and global-law claims.

\paragraph{Readback.}
The carrier reads back to observable data by following the curated ORF interval dataset pointer, the NCBI RefSeq GenBank XML provenance pointer, the NCBI genetic-code table pointer used by the classifier, the claim record `h2.orf\_eligibility.curated\_interval\_contact`, the linked conjecture `orf\_eligibility.seed.boundary`, and the passed `curated\_orf\_interval\_contact\_validation` experiment run. The readback surface is a finite path from externally curated nucleotide intervals and matched controls to classifier outputs under a frozen start/stop-window enumeration. It records contact between a bounded geometry-only classifier and a curated interval dataset; it does not claim that the geometry translates, folds, functions, is physically admissible, or supplies a universal biological law.

\paragraph{Derivation from coordinate, closure, spectrum, and relation.}
The internal newmath/BEDC content is a pure finite-coordinate packet: a BioReality-facing carrier name, a codon-window partition slot, a median-closure context slot, a spectrum context slot, a quotient-context slot, a classifier-rule slot, an experiment-run provenance slot, and a boundary slot. The BEDC side may express finite geometry, carrier alignment, field separation, and TasteGate-style readback discipline. It may also record that upstream codon topology, median closure, spectrum, and quotient geometry are context, not biological realization. No curated RefSeq interval, genetic-code table row, nucleotide sequence, start position, stop position, acceptance rate, rejection rate, split result, p-value, or row count is a kernel fact; those values are not BEDC kernel facts. Those items remain bridge and provenance fields supplied by external reality sources.

\paragraph{Curated reality contacts and observed facts.}
- Curated interval dataset pointer: `tools/bio\_reality/data/curated\_orf\_interval\_contact\_dataset.json`, cited as the external ORF interval contact dataset for this claim. - Curated NCBI RefSeq source pointer: NCBI RefSeq GenBank XML CDS intervals from the Escherichia coli K-12 MG1655 complete genome accession `NC\_000913.3`, cited by dataset provenance rather than copied into the BEDC carrier. - Curated genetic-code table pointer: `tools/bio\_reality/data/ncbi\_genetic\_codes.json`, cited as the external table source used by start/stop enumeration. - Claim pointer: `tools/bio\_reality/registries/claims.json` record `h2.orf\_eligibility.curated\_interval\_contact`. - Conjecture pointer: `tools/bio\_reality/inbox/conjectures.jsonl` record `orf\_eligibility.seed.boundary`. - Experiment provenance pointer: `tools/bio\_reality/state/experiment\_runs.jsonl` latest passed `experiment\_run\_id` `7c9b30b02d46` for claim `h2.orf\_eligibility.curated\_interval\_contact`. - Dataset-load witness: experiment check `curated\_interval\_dataset\_loaded`. - Protocol-freeze witness: experiment check `protocol\_frozen\_before\_external\_observation`. - Input-class witness: experiment check `required\_input\_classes\_present`. - Frozen-classifier witness: experiment check `classifier\_frozen\_and\_geometry\_only`. - Positive-contact statistical witness: experiment check `positive\_interval\_strong\_binomial`. - Matched-decoy statistical witness: experiment check `matched\_decoy\_rejection\_strong\_binomial`. - Boundary-control witness: experiment check `boundary\_cases\_not\_promoted`. - Heldout-stability witness: experiment check `heldout\_split\_stability`. - Paired-baseline witness: experiment check `predeclared\_baseline\_pairwise\_advantage`. - Cannot-claim witness: experiment check `no\_geometry\_to\_higher\_layer\_promotion`. - External numeric values from these witnesses remain provenance fields for the bridge; they are not internalized as BEDC kernel facts.

\paragraph{Layer discipline and out-of-scope assertions.}
- This chapter does not claim biological-code necessity. - This chapter does not claim that codon/window geometry establishes translation. - This chapter does not claim that curated ORF interval contact establishes ribosome-mediated translation realization. - This chapter does not claim protein folding, structural order, physical admissibility, biological function, biochemical mechanism, or universal biological mechanism. - This chapter does not claim that the frozen classifier applies outside the curated dataset and declared controls. - This chapter does not claim that matched decoy rejection or boundary non-promotion classifies biological windows beyond this external contact scope. - This chapter does not claim that NCBI RefSeq intervals, NCBI genetic-code rows, nucleotide sequences, row classes, split labels, statistical witnesses, p-values, or experiment-run outputs are BEDC kernel facts. - This chapter does not promote median closure, quotient geometry, spectrum, or start/stop enumeration into a higher biological layer without a separate reality contact for that layer.

\paragraph{Disclaimer on the bridge from coordinate to mechanism.}
This proposal is a vision-level scientific-model bridge for a stable BioReality ORF-eligibility interval-contact claim. It is not a CheckedCert claim about molecular biology, and it does not turn a BEDC coordinate, codon-window geometry, median closure, quotient context, spectrum, curated RefSeq interval, NCBI genetic-code table, frozen classifier, or statistical witness into translation realization, folded structure, physical admissibility, biological function, biological-code necessity, mechanism, or a universal biological law. The proposal records only an ORF-eligibility-layer readback from explicitly external curated inputs, with every higher biological layer blocked until separately contacted.

\paragraph{Lean-side statement target sketch.}
`BEDC.Derived.RealityBoundCodonTopologyOrfIntervalContactLedgerUp.TasteGate` carrier alignment, with curated-interval dataset, NCBI RefSeq provenance, genetic-code table, experiment-run, heldout-stability, statistical-witness, and cannot-claim evidence represented only as bridge/provenance fields.

