\origin{ai}
\subsection{A finite B-star Q6 coupling contact for translation readout survival}
\label{sec:b-star-q6-coupling-contact}

\paragraph{Question.}
The record tests whether the nine residual coordinates of $B^{\ast}_{Q6}$ remain visible after the amino-acid quotient is imposed.  The intended survival object is a matrix $S_{ij}=S_{q_i}(r_j\mid Z)$, where the row coordinate $q_i$ is one of the nine synonymous residual directions and the readout $r_j$ is a translation-related measurement such as tAI, stAI, ribosome occupancy, translation efficiency, or protein abundance.  The control set is
$$
\begin{aligned}
Z &= (\text{amino-acid composition},\ \text{organism context},\ \mathrm{GC3},\ \text{coding length},\ \text{$M$-density baseline}).
\end{aligned}
$$
The finite computation available here is not yet the full survival matrix.  It is a coupling contact against a proxy readout, namely the tRNA-Leu CUN-versus-UUR log-copy spectrum.  It therefore tests whether the residual coordinates can couple to a translation-adjacent codon-readout spectrum, while leaving the stronger translation-survival assertion open until direct tAI, stAI, ribosome-profiling, mRNA, or proteomics contacts are attached.

\paragraph{Finite carrier.}
The codon-count ambient space has $61$ sense-codon coordinates.  Inside this space the computation formed the following nine $B^{\ast}_{Q6}$ synonymous residual rows:
$$
\begin{aligned}
&\mathrm{Arg}_{\mathrm{AGR}},\quad \mathrm{Ile}_{\mathrm{AUA}},\quad K_{\mathrm{AAA}},\quad
\mathrm{Leu}_{\mathrm{CUN}\,/\,\mathrm{UUR}},\quad
\mathrm{Leu}_{\mathrm{UUA}\,/\,\mathrm{UUG}},\\
&\mathrm{Ser}_{\mathrm{UCA}\,/\,\mathrm{UCG}},\quad
\mathrm{Ser}_{\mathrm{UCR}\,/\,\mathrm{AGY}},\quad
\mathrm{Thr}_{\mathrm{ACR}\,/\,\mathrm{ACY}},\quad
f_3\text{-stress}.
\end{aligned}
$$
The organisms loaded in the finite row set were $\mathrm{Homo\ sapiens}$, $\mathrm{Saccharomyces\ cerevisiae}$, and $\mathrm{Escherichia\ coli\ K12}$.  Thus the evidence is a three-organism computation, not a population estimate.  The run identifier was $4a783972e74b$, and the finite readback was recorded at $2026$-$06$-$01$T$00$:$28$:$36$+00:$00$.

\paragraph{Coupling statistic.}
For a residual coordinate $q_i$ and a readout weight $\ell_j$, the contact uses the synonymous projection $\ell_j^{\perp}$ and computes the covariance coupling
$$
\begin{aligned}
A_{ij} &= q_i^{T}\Sigma\ell_j^{\perp}.
\end{aligned}
$$
The stated null condition for this finite coupling run was
$$
\begin{aligned}
|A_{ij}| &< 0.01\quad\text{for all nine residual coordinates against the proxy readout}.
\end{aligned}
$$
That null condition was not met.  The threshold was $0.01$, the number of nonzero entries above the reported criterion was $9$, and the maximum absolute coupling was
$$
\begin{aligned}
\max_{i,j}|A_{ij}| &= 1882464.1106377328.
\end{aligned}
$$
The finite fact is therefore that every one of the nine listed residual coordinates produced a nonzero proxy-coupling entry in this three-organism contact.  This establishes a codon-usage-topology signal against the available tRNA-copy spectrum; it does not by itself establish survival of any row in the controlled translation matrix $S_{ij}$.

\paragraph{Survival target.}
The intended survival score compares a model with the residual coordinate to the corresponding controlled baseline.  In partial-correlation language, a row survives only if it improves the residual description of a direct readout after $Z$ has already been supplied.  In minimum-description language, the same requirement is that adding $q_i$ reduces the description length of $r_j$ after the amino-acid, organism, GC3, length, and $M$-density controls have been charged.  The support condition for the stronger claim is therefore
$$
\begin{aligned}
S_{ij} &> 0
\end{aligned}
$$
for at least one pair $(q_i,r_j)$ under the full control set and after the simpler-codon-baseline ablation.  The current finite contact reports $A_{ij}$ against a proxy spectrum, not $S_{ij}$ against ribosome profiling, tAI, stAI, or abundance data.  Consequently a positive $A_{ij}$ entry is only a candidate direction for survival testing; it is not promoted to a positive survival score without the controlled partial-$R^2$ or description-length calculation.

\paragraph{Readout boundary.}
The attached data support a bounded statement: in the $61$-codon count space, across the three loaded organisms, the nine named $B^{\ast}_{Q6}$ residual coordinates were computable and did not vanish against the tRNA-Leu CUN-versus-UUR log-copy proxy under the $0.01$ coupling break condition.  The record does not infer ribosome-mediated translation from codon counts and tRNA gene-copy ratios alone.  It also does not infer folding, physical admissibility, biological function, biochemical mechanism, pathway involvement, or a universal biological law.  A separate contact must supply the relevant observation before any such layer can be discussed: ribosome profiling or matched mRNA abundance for translation efficiency, tAI or stAI weights for codon-adaptation readouts, and matched proteomics for protein abundance.  The sign of an entry in this three-organism matrix is likewise not a universal directionality claim.

\paragraph{Interpretation.}
The contact is best read as a finite non-absorption test for the residual coordinate system at the codon-usage-topology layer.  The amino-acid quotient was kept explicit through the synonymous projection, and the finite proxy matrix failed the all-small-coupling null.  This makes the $B^{\ast}_{Q6}$ rows eligible for a controlled translation-survival assay, but it leaves the survival verdict itself pending until direct translation readouts and the full $Z$ controls are jointly present.  The chapter therefore records a concrete coupling contact and a precise next test: construct the $9\times K$ matrix of $S_{ij}$ values on organism-matched tAI, stAI, ribosome-occupancy, translation-efficiency, and protein-abundance readouts, then report which entries remain positive, zero, or negative after the controls and baseline ablation.