\section{Distinction and History}
\label{sec:visions-philosophy-distinction-and-history}

BEDC philosophy is the disciplined reading of the following generative
chain:
$$
\begin{gathered}
\Mark \to \Hist \to \hsame \to \Ext/\Cont \to
\Ask/\Sig \to \Pkg/\Gap \to \NameCert \to
\text{mature interface}.
\end{gathered}
$$
The reading does not add a metaphysics to the finite kernel. It asks
which entities may be called objects, knowledge, observation, subject,
time, world, causality, consciousness, or boundary, once every such
claim is forced to pass through generated histories, licensed
classifiers, witness ledgers, and naming certificates.

\begin{definition}[Auditable generativity]
\label{def:philosophy-auditable-generativity}
Auditable generativity is the position that every mature object is a
licensed name rather than a primitive, every item of knowledge is a
traceable witness rather than bare possession of truth, every observer
is a history rather than a hidden substance, every time parameter is
history growth rather than an external container, and every commitment
exceeding a closed substrate must be exposed as a \(\Gap\) or boundary
position rather than consumed as an internal theorem.
\end{definition}

\begin{theorem}[Philosophy is not an additional layer]
\label{thm:philosophy-not-additional-layer}
The philosophical reading of BEDC is a consequence of the kernel
signature and certificate discipline, not an auxiliary doctrine placed
above them.
\end{theorem}
\begin{proof}
The continuation relation has only history-valued endpoints, the kernel
identity criterion for histories is internal history-sameness, and the
forward direction of continuation is fixed by the constructive
formation of histories. A separate observer-substance, a global truth
predicate, or an unledgered mature object would require a carrier or
transport not supplied by the kernel. The philosophical reading is
therefore obtained by spelling out which commitments are already
encoded by the available signatures and which commitments must remain
outside the object layer as exposed boundary positions.
\end{proof}

\subsection{Primitive distinction}
\label{subsec:primitive-distinction}

\begin{definition}[Primitive marks]
\label{def:philosophy-primitive-marks}
The primitive marks of BEDC are two emission results, denoted
\(\bzero : \Mark\) and \(\bone : \Mark\). They are not natural
numbers, truth values, Boolean objects, or elements of a presupposed
set. They are only the minimal object-language marks from which
distinguishable emission histories may be generated.
\end{definition}

\begin{definition}[Primitive distinction]
\label{def:philosophy-primitive-distinction}
The primitive distinction is the closed mark-level separation between
\(\bzero\) and \(\bone\): the internal sameness relation generates the
diagonal judgments for each mark and does not generate a cross-mark
sameness judgment. Philosophically, the point is not that two prior
objects are given, but that distinguishability itself is the lowest
condition of later object formation.
\end{definition}

\begin{theorem}[Primitive distinction is irreducible]
\label{thm:philosophy-primitive-distinction-irreducible}
The primitive distinction cannot be reduced inside BEDC to a simpler
internal structure.
\end{theorem}
\begin{proof}
Any proposed reduction would have to say how a lower structure
distinguishes inputs from outputs, success from failure, and the same
case from a different case. That act of discrimination already
presupposes a distinction. Iterating the reduction therefore either
never starts or accepts a lowest closed discrimination. BEDC takes the
mark-level constructor separation as that closed ground loop.
\end{proof}

\begin{corollary}[Distinction precedes information]
\label{cor:philosophy-distinction-precedes-information}
Information is not prior to distinction in BEDC.
\end{corollary}
\begin{proof}
Information requires that one state, mark, or trace be separable from
another. Without the mark-level separation there is no separation
between the two history constructors, hence no recorded sequence, no
classifier output, and no ledgered information. Distinction is
therefore a precondition for information rather than a species of
information.
\end{proof}

\begin{corollary}[The starting point is not a thing]
\label{cor:philosophy-starting-point-not-thing}
The ontological starting point of BEDC is not an object, set, subject,
or proposition, but recordable distinguishability.
\end{corollary}
\begin{proof}
Objects require identity conditions. Identity conditions require a
contrast between sameness and difference. The mark layer supplies that
contrast before mature objects are licensed. Hence objects arise only
after distinction has entered histories and certificates.
\end{proof}

\subsection{Mark sameness}
\label{subsec:mark-sameness}

\begin{definition}[Internal mark sameness]
\label{def:philosophy-internal-mark-sameness}
The relation \(\msame(m,n)\) is the object-language sameness judgment
for marks. It is generated by the two diagonal cases for \(\bzero\) and
\(\bone\), with no constructor producing \(\msame(\bzero,\bone)\) or
\(\msame(\bone,\bzero)\).
\end{definition}

\begin{definition}[Internal sameness is not host equality]
\label{def:philosophy-mark-sameness-not-host-equality}
The relation \(\msame\) is an internal BEDC judgment. It is not host
definitional equality, not set-theoretic equality, and not an
unrestricted external equality oracle.
\end{definition}

\begin{theorem}[Mark sameness is reflexive]
\label{thm:philosophy-mark-sameness-reflexive}
For every generated mark \(m\), the judgment \(\msame(m,m)\) is
generated.
\end{theorem}
\begin{proof}
The closed mark carrier has only the two generated marks. In the
\(\bzero\) case the corresponding diagonal rule gives
\(\msame(\bzero,\bzero)\); in the \(\bone\) case the corresponding
diagonal rule gives \(\msame(\bone,\bone)\).
\end{proof}

\begin{theorem}[Mark sameness is symmetric and transitive]
\label{thm:philosophy-mark-sameness-symmetric-transitive}
The internal mark-sameness judgment is symmetric and transitive.
\end{theorem}
\begin{proof}
Every generated mark-sameness derivation is diagonal. Reversing a
diagonal judgment gives the same diagonal judgment, so symmetry holds.
Composing two generated judgments through a middle mark can only remain
on the same diagonal, so transitivity holds.
\end{proof}

\begin{theorem}[Mark no-confusion]
\label{thm:philosophy-mark-no-confusion}
BEDC does not generate a cross-mark sameness judgment between
\(\bzero\) and \(\bone\).
\end{theorem}
\begin{proof}
The generation rules for \(\msame\) contain only the diagonal judgments.
There is no cross-mark constructor and no closure rule that converts a
diagonal judgment into a cross-mark judgment.
\end{proof}

\begin{corollary}[Primitive marks are not completed Booleans]
\label{cor:philosophy-primitive-marks-not-booleans}
The primitive marks must not be read as an already available Boolean
interface.
\end{corollary}
\begin{proof}
A Boolean interface is a mature data interface with its own carrier,
classifier, stability behavior, and naming certificate. The primitive
marks are earlier than such an interface. Reading them directly as
Booleans would import a mature object at the ground layer instead of
deriving it through the certificate discipline.
\end{proof}

\subsection{History formation}
\label{subsec:history-formation}

\begin{definition}[Histories]
\label{def:philosophy-histories}
The carrier \(\Hist\) is generated by the empty history \(\emp\) and
the two extension constructors \(\Ezero\) and \(\Eone\). The public
reading is that \(\emp\) records no distinction, while
\(\Ezero(h)\) and \(\Eone(h)\) record one additional mark-shaped
emission above \(h\).
\end{definition}

\begin{definition}[Information content of a history]
\label{def:philosophy-history-information-content}
The information content of a history is the finite distinction trace
recovered by recursion on its generated form. The empty history has the
empty trace; an \(\Ezero\)-extension appends the \(\bzero\)-shaped tag;
an \(\Eone\)-extension appends the \(\bone\)-shaped tag. These tags are
metalinguistic readings of constructor shape, not imported natural
numbers or Boolean values.
\end{definition}

\begin{theorem}[Histories are finitely generated]
\label{thm:philosophy-histories-finitely-generated}
Every generated history is obtained from \(\emp\) by finitely many
applications of \(\Ezero\) and \(\Eone\).
\end{theorem}
\begin{proof}
The closed formation rules for \(\Hist\) provide only the empty
constructor and the two extension constructors. Following the
constructor tree of any generated history downward therefore reaches
\(\emp\) after finitely many predecessor steps.
\end{proof}

\begin{corollary}[No external history in the kernel]
\label{cor:philosophy-no-external-history-kernel}
There is no kernel history not generated by \(\emp\), \(\Ezero\), and
\(\Eone\).
\end{corollary}
\begin{proof}
An external history would require an additional constructor or an
additional import rule. Neither is part of the closed kernel carrier.
\end{proof}

\begin{theorem}[The empty history is a zero-information boundary]
\label{thm:philosophy-empty-history-zero-information-boundary}
The empty history records no distinction.
\end{theorem}
\begin{proof}
By the recursion defining history information content, \(\emp\) is the
base case and contributes no constructor tag. It is therefore the
boundary at which no distinction has yet entered a history.
\end{proof}

\begin{corollary}[Nontrivial information requires extension]
\label{cor:philosophy-nontrivial-information-requires-extension}
Any history with nonempty information content has the form
\(\Ezero(k)\) or \(\Eone(k)\) for some history \(k\).
\end{corollary}
\begin{proof}
If a history is \(\emp\), its information content is empty. Every
generated nonempty history must therefore arise by one of the two
extension constructors.
\end{proof}

\subsection{History sameness}
\label{subsec:history-sameness}

\begin{definition}[Internal history sameness]
\label{def:philosophy-internal-history-sameness}
The judgment \(\hsame(h,k)\) is the object-language sameness relation
for histories. It is generated by the empty diagonal case and by
constructor-respecting closure through \(\Ezero\) and \(\Eone\). It has
no generation rule comparing an empty history with an extension, or an
\(\Ezero\)-extension with an \(\Eone\)-extension.
\end{definition}

\begin{definition}[History identity]
\label{def:philosophy-history-identity}
The identity of a history, inside BEDC, is its internal history
sameness profile. It is not supplied by a host equality oracle.
\end{definition}

\begin{theorem}[History sameness is reflexive]
\label{thm:philosophy-history-sameness-reflexive}
For every generated history \(h\), the judgment \(\hsame(h,h)\) is
generated.
\end{theorem}
\begin{proof}
Induct on the generated form of \(h\). The empty case is the empty
diagonal rule. The \(\Ezero\) and \(\Eone\) cases follow by applying
the corresponding constructor-respecting closure to the induction
hypothesis.
\end{proof}

\begin{theorem}[History sameness is symmetric and transitive]
\label{thm:philosophy-history-sameness-symmetric-transitive}
The internal history-sameness judgment is symmetric and transitive.
\end{theorem}
\begin{proof}
Symmetry follows by induction on the generated sameness derivation:
the empty case reverses to itself, and each constructor-respecting case
uses the induction hypothesis below the same constructor. Transitivity
follows by induction on one sameness derivation and inversion on the
other; the closed generation rules permit only matching constructors,
after which the induction hypothesis composes the predecessor
judgments.
\end{proof}

\begin{theorem}[History no-confusion]
\label{thm:philosophy-history-no-confusion}
The kernel does not generate history-sameness judgments between
\(\emp\) and an extension, nor between an \(\Ezero\)-extension and an
\(\Eone\)-extension.
\end{theorem}
\begin{proof}
The generation rules for \(\hsame\) contain only the empty diagonal,
the \(\Ezero\)-respecting closure, and the \(\Eone\)-respecting
closure. None of these generates a cross-shape judgment.
\end{proof}

\begin{corollary}[History identity is constructor-shape identity]
\label{cor:philosophy-history-identity-constructor-shape}
An internal sameness judgment between two \(\Ezero\)-extensions must
come from an internal sameness judgment between their predecessors, and
similarly for two \(\Eone\)-extensions.
\end{corollary}
\begin{proof}
This is the inversion principle for the two constructor-respecting
generation rules of \(\hsame\).
\end{proof}

\subsection{Minimal information carrier}
\label{subsec:minimal-information-carrier}

\begin{definition}[Binary-distinction information carrier]
\label{def:philosophy-binary-distinction-information-carrier}
A binary-distinction information carrier is a carrier that represents
two different step shapes and finite traces assembled from those steps.
\end{definition}

\begin{theorem}[Hist is the minimal binary-distinction carrier]
\label{thm:philosophy-hist-minimal-binary-distinction-carrier}
The carrier \(\Hist\) is the minimal BEDC carrier for binary-distinction
information.
\end{theorem}
\begin{proof}
\(\Hist\) has exactly an empty origin and two extension shapes, so it
can record every finite trace of two mark-shaped distinctions. Removing
the empty origin leaves no start for trace formation. Removing either
extension shape destroys binary distinction. Identifying the two
extension shapes violates history no-confusion and erases the
difference to be recorded. Thus any weaker carrier fails to represent
binary-distinction information.
\end{proof}

\begin{corollary}[Information requires history]
\label{cor:philosophy-information-requires-history}
Every nontrivial item of information available to the BEDC object layer
must leave a trace in a history or in a derived ledger certified from
histories.
\end{corollary}
\begin{proof}
Nontrivial information requires a distinction, and a usable distinction
must enter a generated trace or a certified structure derived from such
a trace. A classifier, signature, or naming certificate may organize
the trace, but it does not bypass the historical condition.
\end{proof}

\begin{corollary}[No bare information]
\label{cor:philosophy-no-bare-information}
BEDC does not accept information that is unhistoried, unwitnessed, and
unledgered.
\end{corollary}
\begin{proof}
If the purported information is usable in the object layer, it must be
distinguishable from its absence or from a different information item.
That distinction must be recorded or certified. If it enters neither a
history nor a derived ledger, the object layer has no licensed way to
consume it.
\end{proof}

\subsection{Prefix order and the preparatory form of time}
\label{subsec:prefix-order-time-preparation}

\begin{definition}[Distinction step]
\label{def:philosophy-distinction-step}
A distinction step is a single application of \(\Ezero\) or \(\Eone\)
to a history.
\end{definition}

\begin{definition}[History prefix]
\label{def:philosophy-history-prefix}
A history \(p\) is a prefix of a history \(h\) when \(h\) is obtained
from \(p\) by a finite trace of distinction steps.
\end{definition}

\begin{theorem}[History generation carries a prefix order]
\label{thm:philosophy-history-generation-prefix-order}
Every nonempty generated history has a direct predecessor shape, and
that predecessor is its immediate prefix.
\end{theorem}
\begin{proof}
By closed generation, a nonempty history is either an \(\Ezero\)- or
\(\Eone\)-extension of a predecessor. History no-confusion prevents the
two shapes from being internally identified and prevents either shape
from being internally identified with \(\emp\). The outer constructor
therefore determines the direct predecessor shape.
\end{proof}

\begin{corollary}[Histories are not sets]
\label{cor:philosophy-histories-are-not-sets}
Histories are generated traces, not sets of already available elements.
\end{corollary}
\begin{proof}
Set-theoretic reading begins from a domain of elements and membership.
BEDC begins from a generated empty history and constructor growth.
History identity is governed by constructor shape and internal
\(\hsame\), not by external membership.
\end{proof}

\begin{corollary}[The lowest form of time is history growth]
\label{cor:philosophy-lowest-form-time-history-growth}
Once a distinction step is read as history growth, the lowest form of
time is already present.
\end{corollary}
\begin{proof}
Time minimally requires before and after. In the kernel, before and
after first appear as the generated movement from a predecessor history
to an \(\Ezero\)- or \(\Eone\)-extension. This gives the preparatory
form later made explicit by the continuation relation.
\end{proof}

\subsection{Synthesis}
\label{subsec:distinction-history-synthesis}

\begin{definition}[Distinction-history chain]
\label{def:philosophy-distinction-history-chain}
The distinction-history chain is the path from primitive mark
separation, through internal mark sameness and no-confusion, to
generated histories, internal history sameness, and recoverable
information content.
\end{definition}

\begin{theorem}[Distinction generates history, history carries information]
\label{thm:philosophy-distinction-generates-history-carries-information}
In BEDC, the lowest auditable form of information is a finite history
generated from primitive distinction.
\end{theorem}
\begin{proof}
Primitive marks supply the first separation. Internal mark sameness and
mark no-confusion provide the object-language identity profile for that
separation. The constructors \(\emp\), \(\Ezero\), and \(\Eone\) record
the separation into finite histories. Internal history sameness and
history no-confusion preserve the generated shape of those records.
History information content is then recovered as the finite trace of
recorded distinctions. Therefore the first auditable information in the
object layer is generated history.
\end{proof}

\begin{corollary}[Ontology begins with recordable distinction]
\label{cor:philosophy-ontology-begins-recordable-distinction}
The first ontological commitment of BEDC is not that things exist, but
that distinctions can be recorded.
\end{corollary}
\begin{proof}
Mature objects require naming certificates; naming certificates require
source, pattern, classifier, stability, and ledger fields; those fields
ultimately depend on generated histories and the distinction structure
that histories record. Hence object talk is downstream from recordable
distinction.
\end{proof}

\begin{corollary}[Passage to continuation]
\label{cor:philosophy-passage-to-continuation}
After distinction enters history, the next philosophical question is
continuation, because a history is not merely a static trace but a
trace capable of generated extension.
\end{corollary}
\begin{proof}
The history carrier records distinction. To account for observation,
time, action, and object formation, the framework must also account for
the passage from one history to another. That passage is exactly the
role of \(\Cont\) at the next layer.
\end{proof}
