\section{Objects, Knowledge, and Naming Certificates}
\label{sec:visions-philosophy-object-knowledge-namecert}

The first layer reads distinction as the condition of history. The
second layer reads continuation as observation, time, and observer
identity. The present layer asks how stable patterns in histories,
continuations, signatures, packages, and gaps become objects and
knowledge. Its compressed thesis is:
$$
\begin{gathered}
\text{object}=\text{licensed name},\\
\text{knowledge}=\text{auditable witness},\\
\text{definition}=\text{certificate for stable generated behavior}.
\end{gathered}
$$
Thus BEDC does not begin with mature objects and then describe them. It
generates histories, classifies stable behavior, records the hidden
material in ledgers, and licenses names only after the relevant
certificate fields are supplied.

\subsection{Objects are not primitive}
\label{subsec:philosophy-objects-not-primitive}

\begin{definition}[Bare object]
\label{def:philosophy-bare-object}
A name \(N\) is a bare object name when it is introduced into the
theory without a displayed source specification, pattern
specification, classifier specification, stability certificate, and
ledger policy. A name such as natural number, real number, set, type,
function, limit, or circle is bare in this sense whenever it is not
accompanied by a certificate explaining how it is generated from BEDC
materials and how its behavior is classified, stabilized, and tracked.
\end{definition}

\begin{definition}[Mature object]
\label{def:philosophy-mature-object}
A mature object is a licensed derived interface. For a proposed name
\(N\), maturity means that \(N\) is accepted through a naming
certificate rather than supplied as a kernel primitive.
\end{definition}

\begin{theorem}[Anti-primitive principle]
\label{thm:philosophy-anti-primitive-principle}
No mature object enters BEDC as a kernel primitive.
\end{theorem}
\begin{proof}
The kernel begins with marks, histories, internal sameness judgments,
continuations, asking events, signatures, packages, gaps, and naming
certificates. Traditional mathematical interfaces such as equality,
functions, natural numbers, arithmetic operations, limits, real
numbers, geometric figures, and folds occur only after the relevant
carrier, classifier, stability, and ledger obligations have been
displayed. They are outputs of the certificate discipline, not inputs
to the finite kernel.
\end{proof}

\begin{corollary}[Definitions do not create objects ex nihilo]
\label{cor:philosophy-definitions-do-not-create-objects}
A definition does not produce an object from nothing; it names stable
generated behavior under a certificate.
\end{corollary}
\begin{proof}
Without a source specification, the proposed name has no generated
material. Without a pattern specification, it has no stable behavior.
Without a classifier, it has no internal same-object condition. Without
a stability certificate, it cannot be reused, descended, composed, or
sealed. Without a ledger policy, its hidden material is not auditable.
The definition becomes object-forming only when these obligations are
met.
\end{proof}

\begin{corollary}[Object existence is certificate existence]
\label{cor:philosophy-object-existence-certificate-existence}
For a mature BEDC object, object-layer existence entails the presence
of an auditable naming certificate.
\end{corollary}
\begin{proof}
A mature object is a licensed name, and a licensed name is not a
primitive input. Its object-layer standing is therefore mediated by the
certificate that licenses it.
\end{proof}

\subsection{The five fields of a naming certificate}
\label{subsec:philosophy-namecert-five-fields}

\begin{definition}[Source specification]
\label{def:philosophy-source-specification}
The source specification of a proposed name \(N\) records the generated
material from which the name receives its license. Its sources may
include raw marks, histories, bundles, signatures, packages, gaps, or
previously licensed names.
\end{definition}

\begin{definition}[Pattern specification]
\label{def:philosophy-pattern-specification}
The pattern specification records the stable behavior that the proposed
name is meant to expose: repetition, continuation, signature
classification, package stability, compatible threading, or another
displayed regularity in the source material.
\end{definition}

\begin{definition}[Classifier specification]
\label{def:philosophy-classifier-specification}
The classifier specification states how source material is grouped
under the proposed name. It answers when two source rows count as the
same \(N\)-object, when two behaviors instantiate the same pattern, and
when two representatives are the same only through a licensed
classifier.
\end{definition}

\begin{definition}[Stability certificate]
\label{def:philosophy-stability-certificate}
The stability certificate records the closure, reuse, descent,
composition, or sealing behavior that makes the name stable enough for
later use. Different interfaces may require different combinations of
these stability modes.
\end{definition}

\begin{definition}[Ledger policy]
\label{def:philosophy-ledger-policy}
The ledger policy records what the name hides and how the hidden
material remains traceable after compression, packaging, projection, or
sealing. It specifies the relevant gap ledger, composite gap, tail
ledger, phase ledger, source ledger, or other derived ledger surface.
\end{definition}

\begin{definition}[Naming certificate]
\label{def:philosophy-naming-certificate}
A paper-level naming certificate for a proposed interface \(N\) is the
five-field packet
$$
\begin{gathered}
\NameCert(N)=
(\mathsf{SourceSpec}_{N},
 \mathsf{PatternSpec}_{N},
 \mathsf{ClassifierSpec}_{N},
 \mathsf{StabilityCert}_{N},
 \mathsf{LedgerPolicy}_{N}).
\end{gathered}
$$
The name \(N\) is licensed only when the required fields of this packet
are supplied.
\end{definition}

\begin{theorem}[The five fields are irreducible]
\label{thm:philosophy-namecert-five-fields-irreducible}
No field of a naming certificate can be omitted without losing the
object's auditable standing.
\end{theorem}
\begin{proof}
Without source, the name has no generated material. Without pattern,
the name has no stable behavior to expose. Without classifier, there is
no internal sameness condition for the named interface. Without
stability, the name cannot be safely reused or transported. Without a
ledger policy, compression loses provenance. The five fields therefore
correspond to source, pattern, sameness, stability, and memory.
\end{proof}

\begin{corollary}[Objects are fivefold qualifications]
\label{cor:philosophy-objects-fivefold-qualifications}
A BEDC object is not a single bare entity but a source-qualified,
pattern-stabilized, classifier-organized, stability-certified, and
ledger-tracked interface.
\end{corollary}
\begin{proof}
The naming certificate licenses the object exactly through those five
fields, and the fields are not optional.
\end{proof}

\subsection{Paper certificates and finite-kernel certificates}
\label{subsec:philosophy-paper-and-kernel-namecert}

\begin{definition}[Paper naming certificate]
\label{def:philosophy-paper-namecert}
A paper naming certificate is the five-field theoretical template that
explains why a proposed interface may be named.
\end{definition}

\begin{definition}[Finite-kernel naming certificate]
\label{def:philosophy-finite-kernel-namecert}
A finite-kernel certificate of the form
\(\mathsf{NameCert}(\mathsf{Carrier},\mathsf{Equiv})\) is a
carrier-and-equivalence certificate over generated histories or their
derived carriers. It supplies inhabitedness of the carrier, reflexivity,
symmetry and transitivity of the equivalence relation, and transport of
carrier membership along that relation.
\end{definition}

\begin{theorem}[Kernel certificates formalize the classifier core]
\label{thm:philosophy-kernel-namecert-classifier-core}
The finite-kernel certificate is the formal core of the paper
\(\NameCert\) at the carrier and classifier layer.
\end{theorem}
\begin{proof}
The paper certificate requires a classifier specification and stability
conditions explaining how a carrier is organized and transported. The
finite-kernel certificate supplies exactly the formal equivalence laws
and membership transport needed for that organization. It does not
exhaust every paper-level semantic field, but it gives the formal
carrier-classifier nucleus of the licensed interface.
\end{proof}

\begin{corollary}[Paper completion is not machine checking]
\label{cor:philosophy-paper-completion-not-machine-checking}
A complete paper certificate is not the same status as a
machine-checked certificate.
\end{corollary}
\begin{proof}
The paper certificate states and argues for the required fields. A
machine-checked certificate requires corresponding formal targets and
auditable acceptance by the checker. The former is a paper obligation
surface; the latter is a verified formal object.
\end{proof}

\subsection{Knowledge as witness}
\label{subsec:philosophy-knowledge-as-witness}

\begin{definition}[BEDC knowledge]
\label{def:philosophy-bedc-knowledge}
To know an object or claim \(X\) in BEDC is to possess a witness for
\(X\). Such a witness may be an \(\msame\) or \(\hsame\) witness, a
\(\Cont\) witness, a signature witness, a package witness, a gap
witness, a naming-certificate witness, a semantic-certificate witness,
or a derivation-certificate witness.
\end{definition}

\begin{definition}[Auditable knowledge]
\label{def:philosophy-auditable-knowledge}
A knowledge item is auditable when its source is visible or
ledger-tracked, its classifier is stated, its stability or transport
law is supplied, its hidden material is recorded by a ledger, and its
proof strength is marked.
\end{definition}

\begin{theorem}[Knowledge is witness, not bare truth]
\label{thm:philosophy-knowledge-witness-not-bare-truth}
The BEDC form of knowledge is witness possession, not an internal bare
truth predicate.
\end{theorem}
\begin{proof}
Object knowledge requires a naming certificate. Classification
knowledge requires a classifier witness. Compressed knowledge requires
a ledger exposing the source material behind the token. Formal
knowledge requires a target accepted by the relevant audit. A claim
without a witness has no public object-layer standing, because the
object layer has no global truth predicate through which it could be
consumed.
\end{proof}

\begin{corollary}[Truth remains meta, certificates enter the object layer]
\label{cor:philosophy-truth-meta-certificates-object-layer}
BEDC object-layer operations consume certificates rather than a total
truth predicate.
\end{corollary}
\begin{proof}
A total internal truth predicate would classify arbitrary propositions
at once. BEDC instead licenses local interfaces through source,
classifier, stability, and ledger witnesses. The object layer operates
with those certificates.
\end{proof}

\subsection{Packaging, compression, and gaps}
\label{subsec:philosophy-packaging-compression-gaps}

\begin{definition}[Package token]
\label{def:philosophy-package-token}
A package judgment \(\Pkg(\Pi,s,p)\) says that, under bundle \(\Pi\),
the answer-history \(s\) is represented by the package token \(p\).
The relation \(\mathsf{psame}(p,q)\) is the internal sameness judgment
for package tokens.
\end{definition}

\begin{definition}[Package policy]
\label{def:philosophy-package-policy}
A package policy supplies existence of tokens for generated
answer-histories, extensionality of tokens along history-sameness,
grounding of package-token sameness in represented histories, and the
visibility rule that only the token and its ledger appear at the
package interface.
\end{definition}

\begin{theorem}[Packages are not quotients]
\label{thm:philosophy-packages-not-quotients}
Package tokens are not quotient classes. Quotient-like behavior is a
certified theorem of the package policy, not a primitive.
\end{theorem}
\begin{proof}
If package tokens were quotient classes, the theory would need a
quotient object or a quotient-soundness principle at the point of
introduction. Instead, tokens are introduced by package judgments, and
their sameness is controlled by extensionality and grounding fields.
The visible quotient-like behavior is therefore derived from package
policy rather than imported as a primitive quotient.
\end{proof}

\begin{definition}[Gap ledger]
\label{def:philosophy-gap-ledger}
A gap ledger records which source histories lie behind a visible
package token, signature token, or compressed interface. It is the
memory surface of a compression.
\end{definition}

\begin{definition}[Gap policy]
\label{def:philosophy-gap-policy}
A gap policy exposes provenance and generation witnesses, covers the
admitted source histories by visible gaps, and separates package tokens
when the same source lies behind their gaps.
\end{definition}

\begin{theorem}[Compression must remember]
\label{thm:philosophy-compression-must-remember}
Every BEDC operation that packages, compresses, projects, seals, or
hides generated material must carry a gap ledger.
\end{theorem}
\begin{proof}
Packaging replaces source histories by visible tokens. Without a gap
ledger, the theory loses the internal witness connecting the token to
the histories it hides. The token would then be a free object rather
than a certified compression. A valid compression must therefore retain
provenance through a ledger.
\end{proof}

\begin{corollary}[No amnesic compression]
\label{cor:philosophy-no-amnesic-compression}
BEDC permits compression, but not compression that forgets its source.
\end{corollary}
\begin{proof}
Compression is acceptable only when the visible token remains connected
to its hidden source material by a gap policy. Removing that memory
breaks auditability.
\end{proof}

\subsection{Semantic naming and pattern-ledger transport}
\label{subsec:philosophy-semantic-namecert-transport}

\begin{definition}[Semantic naming certificate]
\label{def:philosophy-semantic-namecert}
A semantic naming certificate is a naming certificate enriched by
source-to-pattern soundness, source-to-ledger soundness, and classifier
transport preserving the pattern and ledger fields.
\end{definition}

\begin{theorem}[Semantic certificates contain pattern and ledger witnesses]
\label{thm:philosophy-semantic-certificates-pattern-ledger-witnesses}
Every semantic naming certificate contains a source witness from which
both the pattern condition and the ledger policy are obtained.
\end{theorem}
\begin{proof}
Eliminating the semantic certificate exposes its core naming
certificate and its pattern and ledger soundness fields. The core
certificate supplies the source witness, and the soundness fields apply
to that same witness.
\end{proof}

\begin{theorem}[Pattern-ledger transport]
\label{thm:philosophy-pattern-ledger-transport}
If a semantic naming certificate classifies a source history \(h\) with
a history \(k\), then the pattern and ledger conditions transport to
\(k\).
\end{theorem}
\begin{proof}
The core naming certificate transports carrier membership along the
classifier relation. Once the target is again recognized as a source
row, the semantic pattern and ledger soundness fields apply at the
target.
\end{proof}

\begin{theorem}[Classifier-chain transport]
\label{thm:philosophy-classifier-chain-transport}
If a semantic certificate supplies classifier links from \(h\) to \(k\)
and from \(k\) to \(r\), and \(h\) carries the source witness, then the
pattern and ledger conditions transport to \(r\).
\end{theorem}
\begin{proof}
Transitivity of the core classifier composes the two links into a
single link from \(h\) to \(r\). Pattern-ledger transport then applies
to that composite link.
\end{proof}

\begin{corollary}[Object stability is transportability]
\label{cor:philosophy-object-stability-transportability}
The stability of a BEDC object is not metaphysical immobility but
transportability of its pattern and ledger across licensed classifier
relations.
\end{corollary}
\begin{proof}
The object remains stable precisely when the certificate can carry its
pattern and ledger through the equivalence or classifier paths that the
interface licenses.
\end{proof}

\subsection{Acceptance gates and strength}
\label{subsec:philosophy-acceptance-gates-strength}

\begin{definition}[Derivation strength]
\label{def:philosophy-derivation-strength}
The strength of a derived object is ordered as
$$
\begin{gathered}
\mathsf{seed}<\mathsf{paperCert}<\mathsf{checkedCert}<\mathsf{bridgeCert}.
\end{gathered}
$$
A seed has a sketched carrier and classifier. A paper certificate fills
the certificate fields in the manuscript. A checked certificate is
backed by formal targets and audit. A bridge certificate adds a
conservative bridge to a standard model.
\end{definition}

\begin{definition}[Acceptance gate]
\label{def:philosophy-acceptance-gate}
For a mature object name \(N\) at strength \(s\), the acceptance gate
is the conjunction of a naming certificate for \(N\) and a derivation
certificate recording that strength.
\end{definition}

\begin{definition}[Derivation certificate]
\label{def:philosophy-derivation-certificate}
A derivation certificate records the source layer carrying \(N\), the
classifier organizing the carrier, exactness of the classifier with
respect to the relevant sameness judgments, the ledger or explicit
absence statement, the stability certificate, and the declared
strength.
\end{definition}

\begin{theorem}[Object export passes through the acceptance gate]
\label{thm:philosophy-object-export-acceptance-gate}
BEDC may export a mature object \(N\) only at a displayed strength
whose acceptance gate is satisfied.
\end{theorem}
\begin{proof}
The naming certificate explains why the name is licensed. The
derivation certificate explains which strength level has been reached.
Without the first, \(N\) is not a licensed name. Without the second, the
theory cannot distinguish a sketch from a paper certificate, a checked
certificate, or a standard-model bridge.
\end{proof}

\begin{corollary}[No strength inflation]
\label{cor:philosophy-no-strength-inflation}
BEDC cannot report a lower strength as a higher one.
\end{corollary}
\begin{proof}
The strength order is cumulative in one direction only. A checked
certificate includes more obligations than a paper certificate, and a
bridge certificate includes more obligations than a checked
certificate. Reporting a lower level as a higher one hides unfinished
certificate obligations.
\end{proof}

\subsection{Synthesis}
\label{subsec:philosophy-object-knowledge-namecert-synthesis}

\begin{theorem}[Object-knowledge-certificate synthesis]
\label{thm:philosophy-object-knowledge-certificate-synthesis}
In BEDC, objects and knowledge enter through certificates:
$$
\begin{gathered}
\text{object}_{N}=\text{licensed name}(N),\\
\text{knowledge}=\text{auditable witness}.
\end{gathered}
$$
The mature object is generated from histories, continuations,
signatures, packages, gaps, and prior names through source, pattern,
classifier, stability, and ledger fields, then exported only at a
declared strength. The knowledge claim appears through a displayed
witness rather than through a bare truth predicate.
\end{theorem}
\begin{proof}
Mature objects are not primitives. A naming certificate has five
irreducible fields. Finite-kernel certificates formalize the
carrier-classifier core. Knowledge is witness possession. Compression
requires a gap ledger. Semantic certificates transport pattern and
ledger along classifiers. Export requires an acceptance gate with a
declared strength. Combining these facts gives the stated synthesis.
\end{proof}

\begin{corollary}[BEDC object theory]
\label{cor:philosophy-bedc-object-theory}
The BEDC theory of objects can be summarized as follows: an object is a
licensed name, a name is a certificate for stable behavior, and a
certificate is the fivefold structure of source, pattern, classifier,
stability, and ledger.
\end{corollary}

\begin{corollary}[BEDC epistemology]
\label{cor:philosophy-bedc-epistemology}
The BEDC theory of knowledge can be summarized as follows: to know is
to hold a witness, to prove is to supply transport, stability, and
ledger data, and to understand an object is to identify the certificate
through which it enters.
\end{corollary}

\begin{corollary}[Passage to logic and meta-loop discipline]
\label{cor:philosophy-passage-to-logic-meta-loop}
Once objects and knowledge are certificate-mediated, the next task is
to identify which proof patterns preserve this discipline and which
patterns smuggle in unwitnessed objects or global truth.
\end{corollary}
\begin{proof}
Certificate discipline accepts local contradiction over fixed carriers,
constructor no-confusion, and witness-preserving transport. It rejects
unwitnessed positive existence, hidden choice, quotient collapse,
propositional extensional collapse, and total truth predicates. The
next philosophical layer must therefore analyze proof and meta-loop
boundaries.
\end{proof}
