\section{Positive Interpretability Discovery}
\label{sec:visions-philosophy-positive-interpretability-discovery}
\origin{ai}

\autoref{sec:visions-philosophy-interpretability-classifier-novelty}
defines classifier novelty as the discovery axis, and
\autoref{sec:visions-philosophy-explanation-complexity-information}
defines net explanation information as benefit minus score and debt.
Positive interpretability discovery is the conjunction of these two
audits: the explanation must introduce a certified classifier shift, and
the shift must pay for its certificate, ledger, and remaining debt under
a public cost protocol.

\begin{definition}[Certified discovery transition]
\label{def:philosophy-certified-discovery-transition}
A transition $E_0\leadsto E_1$ is a certified discovery transition when
it has classifier novelty, the target classifier state has a NameCert,
the changed classifier surface has ledger rows, the classifier shift has
a local or formal witness, and the seal records the not-claimed
boundary.
\end{definition}

\begin{definition}[Positive discovery transition]
\label{def:philosophy-positive-discovery-transition}
A certified discovery transition is positive when
$$
\Delta\mathsf{Info}_{\mathbf w}(E_0,E_1)>0
$$
for the public cost protocol used by the claim. It is negative when the
quantity is below zero and neutral when it is zero.
\end{definition}

\begin{definition}[Strong positive discovery]
\label{def:philosophy-strong-positive-discovery}
A positive discovery transition is strong when the target explanation has
zero critical debt, a scope seal, reproducible classifier and ledger
evidence, a public cost protocol, and a NameCert-compatible NDNA packet.
\end{definition}

\begin{definition}[False positive discovery claim]
\label{def:philosophy-false-positive-discovery-claim}
A claim is a false positive discovery claim when it asserts positive
interpretability discovery while lacking classifier novelty, NameCert,
ledger, positive net explanation information, a public cost protocol, or
a declared not-claimed boundary.
\end{definition}

\begin{theorem}[Positive discovery implies certified discovery]
\label{thm:philosophy-positive-discovery-implies-certified-discovery}
Every positive discovery transition is a certified discovery transition.
\end{theorem}
\begin{proof}
Positive discovery is defined by adding the strict net-information
inequality to certified discovery. Hence all certified-discovery
requirements are inherited.
\end{proof}

\begin{corollary}[Positive discovery requires classifier novelty]
\label{cor:philosophy-positive-discovery-requires-classifier-novelty}
Every positive discovery transition has classifier novelty.
\end{corollary}
\begin{proof}
Certified discovery requires classifier novelty by
\autoref{def:philosophy-certified-discovery-transition}, and positive
discovery implies certified discovery.
\end{proof}

\begin{corollary}[Positive discovery requires NameCert and ledger]
\label{cor:philosophy-positive-discovery-requires-namecert-ledger}
Every positive discovery transition carries NameCert and ledger rows for
the changed classifier surface.
\end{corollary}
\begin{proof}
These rows are part of certified discovery, which every positive
discovery transition satisfies.
\end{proof}

\begin{theorem}[Classifier novelty alone is not positive discovery]
\label{thm:philosophy-classifier-novelty-alone-not-positive-discovery}
Classifier novelty by itself does not imply positive interpretability
discovery.
\end{theorem}
\begin{proof}
A changed classifier can be expensive to source, stabilize, ledger,
intervene on, verify, or seal. It may also lack complete NameCert or
ledger rows. If the net information is nonpositive, or if the certificate
surface is incomplete, the transition is not positive discovery.
\end{proof}

\begin{theorem}[Positive information alone is not discovery]
\label{thm:philosophy-positive-information-alone-not-discovery}
Positive net explanation information does not imply positive
interpretability discovery.
\end{theorem}
\begin{proof}
The net gain can come from ledger completion, lower score, verification
debt reduction, source-scope clarification, semantic-ledger completion,
or a better not-claimed boundary while the classifier relation is
unchanged. Such a transition has no classifier novelty and is therefore
not discovery.
\end{proof}

\begin{theorem}[Ledger completion can be positive without discovery]
\label{thm:philosophy-ledger-completion-positive-not-discovery}
Ledger completion can yield positive net explanation information while
preserving the classifier.
\end{theorem}
\begin{proof}
Completing a critical ledger can lower debt more than it increases
score. If the classifier relation is unchanged, the transition is a
positive audit improvement rather than classifier-level discovery.
\end{proof}

\begin{theorem}[Formal hardening can be positive without discovery]
\label{thm:philosophy-formal-hardening-positive-not-discovery}
Formal hardening can yield positive net explanation information while
preserving the classifier.
\end{theorem}
\begin{proof}
Hardening can lower verification debt and increase reuse. If its gain
exceeds its verification cost while the classifier relation remains
unchanged, it is a positive hardening improvement rather than positive
interpretability discovery.
\end{proof}

\subsection{Cost Protocols}
\label{subsec:philosophy-positive-discovery-cost-protocols}

\begin{definition}[Positive discovery cost protocol]
\label{def:philosophy-positive-discovery-cost-protocol}
A positive discovery cost protocol specifies the benefit functional,
score functional, debt functional, weight profile, source and target
scope, and not-claimed boundary used to evaluate
$\Delta\mathsf{Info}_{\mathbf w}(E_0,E_1)$.
\end{definition}

\begin{definition}[Cost opacity and cost debt]
\label{def:philosophy-cost-opacity-debt}
Cost opacity occurs when a positive discovery claim hides its benefit,
score, debt, weight, scope, or excluded-claim conventions. Cost debt is
the uncounted cost or debt created by omitting a critical term such as
ledger cost, semantic debt, verification debt, intervention debt, or
generalization debt.
\end{definition}

\begin{theorem}[Positive discovery requires protocol completeness]
\label{thm:philosophy-positive-discovery-requires-protocol-completeness}
A positive discovery claim is auditable only when its cost protocol is
complete and public.
\end{theorem}
\begin{proof}
The sign of $\Delta\mathsf{Info}_{\mathbf w}$ depends on benefit, score,
debt, and weights inside a declared scope. If any of these terms is
hidden, the strict positivity claim cannot be checked.
\end{proof}

\begin{theorem}[Cost debt can invalidate positivity]
\label{thm:philosophy-cost-debt-can-invalidate-positivity}
Adding omitted critical cost or debt terms can turn an apparently
positive discovery claim into a nonpositive one.
\end{theorem}
\begin{proof}
Net information subtracts score and debt. If omitted cost or debt is
restored, the computed net gain decreases. When the omitted amount
exceeds the original positive margin, the strict positivity inequality
fails.
\end{proof}

\begin{corollary}[Positive discovery must count critical debts]
\label{cor:philosophy-positive-discovery-counts-critical-debts}
Ledger, semantic, verification, intervention, and generalization debts
must be included whenever they are relevant to the claim.
\end{corollary}
\begin{proof}
These are critical debt classes for interpretability claims. Omitting
them creates cost debt, which can invalidate positivity by
\autoref{thm:philosophy-cost-debt-can-invalidate-positivity}.
\end{proof}

\subsection{Benefit Types}
\label{subsec:philosophy-positive-discovery-benefit-types}

\begin{definition}[Positive discovery benefit modes]
\label{def:philosophy-positive-discovery-benefit-modes}
Positive discovery may be coverage-positive, prediction-positive,
transfer-positive, intervention-positive, unification-positive,
verification-positive, or ledger-positive, according to the benefit term
that principally drives the positive net information inequality.
\end{definition}

\begin{theorem}[Benefit modes can overlap]
\label{thm:philosophy-positive-benefit-modes-overlap}
A positive discovery transition can have several benefit modes at once.
\end{theorem}
\begin{proof}
The benefit functional is a sum of coverage, prediction, transfer,
intervention, verification, and unification terms. More than one term can
make a material contribution to the positive margin.
\end{proof}

\begin{corollary}[Positive discovery should report benefit structure]
\label{cor:philosophy-positive-discovery-report-benefit-structure}
A positive discovery claim should state which benefit terms drive its
positive margin.
\end{corollary}
\begin{proof}
Since benefit modes can overlap and trade off against costs and debts,
reporting only the final sign hides the reason the transition is
positive.
\end{proof}

\subsection{Strong and NDNA-Positive Discovery}
\label{subsec:philosophy-strong-ndna-positive-discovery}

\begin{definition}[NDNA-positive discovery criterion]
\label{def:philosophy-ndna-positive-discovery-criterion}
A transition satisfies the NDNA-positive criterion when it has classifier
novelty, the target NDNA is complete, anchored, NameCert-compatible, and
ledger-complete, and the NDNA-level net information difference is
positive.
\end{definition}

\begin{theorem}[NDNA-positive criterion implies positive discovery]
\label{thm:philosophy-ndna-positive-criterion-implies-positive-discovery}
Every transition satisfying the NDNA-positive criterion is a positive
interpretability discovery.
\end{theorem}
\begin{proof}
Classifier novelty supplies the discovery axis. Complete, anchored,
NameCert-compatible NDNA supplies the certified explanation surface, and
ledger completeness supplies the required ledger. The positive NDNA-level
net information difference supplies the positivity condition.
\end{proof}

\begin{theorem}[NDNA completeness alone is not positive discovery]
\label{thm:philosophy-ndna-completeness-alone-not-positive-discovery}
Complete NDNA alone does not imply positive interpretability discovery.
\end{theorem}
\begin{proof}
Completeness says that all eight loci are present. It does not state that
the classifier differs from the prior classifier, that the NameCert
projection is compatible, or that net explanation information is
positive.
\end{proof}

\begin{theorem}[Strong positive discovery implies positive discovery]
\label{thm:philosophy-strong-positive-implies-positive}
Every strong positive discovery is a positive discovery.
\end{theorem}
\begin{proof}
Strong positive discovery includes positive discovery and adds zero
critical debt, scope sealing, reproducibility, a public cost protocol,
and NameCert-compatible NDNA.
\end{proof}

\begin{theorem}[Positive discovery need not be strong]
\label{thm:philosophy-positive-need-not-be-strong}
A positive discovery transition need not be strong.
\end{theorem}
\begin{proof}
A transition can have classifier novelty, NameCert, ledger, and positive
net information while still retaining noncritical debt, an incomplete
reproducibility package, a partially developed seal, or an unsettled
hardening frontier.
\end{proof}

\subsection{Black-Box Resolution and Verification}
\label{subsec:philosophy-positive-discovery-black-box-verification}

\begin{definition}[Positive black-box resolution]
\label{def:philosophy-positive-black-box-resolution}
A transition is a positive black-box resolution when it lowers
black-box debt by more than the additional explanation score charged to
that resolution inside the declared scope.
\end{definition}

\begin{definition}[Positive discovery-resolution]
\label{def:philosophy-positive-discovery-resolution}
A transition is a positive discovery-resolution when it is both a
positive interpretability discovery and a positive black-box resolution.
\end{definition}

\begin{theorem}[Positive black-box resolution need not be discovery]
\label{thm:philosophy-positive-black-box-resolution-not-discovery}
Positive black-box resolution does not imply interpretability discovery.
\end{theorem}
\begin{proof}
Completing the ledger of an existing classifier can reduce black-box debt
more than it increases score. If the classifier remains unchanged, the
transition resolves black-box residue but does not discover a classifier.
\end{proof}

\begin{theorem}[Positive discovery-resolution is the strongest resolution form]
\label{thm:philosophy-positive-discovery-resolution-strongest}
A positive discovery-resolution both changes the certified classifier
surface and positively reduces black-box debt in net terms.
\end{theorem}
\begin{proof}
The first condition follows from positive interpretability discovery.
The second follows from positive black-box resolution. Thus the
transition improves both the classifier axis and the black-box debt axis.
\end{proof}

\begin{definition}[Verification-assisted positive discovery]
\label{def:philosophy-verification-assisted-positive-discovery}
A positive discovery is verification-assisted when formal hardening
contributes to the positive margin. It is verification-dependent when
removing the verification benefit makes the net information difference
nonpositive.
\end{definition}

\begin{theorem}[Verification assistance does not replace classifier novelty]
\label{thm:philosophy-verification-assistance-not-replace-novelty}
Verification-assisted positive discovery still requires classifier
novelty.
\end{theorem}
\begin{proof}
The verification term can contribute to benefit, but positive discovery
also requires certified classifier shift. A verification-only transition
without classifier novelty is a hardening improvement, not discovery.
\end{proof}

\begin{theorem}[Verification-assisted discovery must count verification cost]
\label{thm:philosophy-verification-assisted-counts-cost}
If formal hardening contributes to a positive discovery claim, then
verification cost and verification-ledger debt must be included.
\end{theorem}
\begin{proof}
Formal hardening can increase benefit, but it also adds proof cost,
dependency cost, trust-boundary obligations, and verification-ledger
residue. Omitting those terms overstates net information.
\end{proof}

\subsection{Lineage and Anti-Laundering}
\label{subsec:philosophy-positive-discovery-lineage-anti-laundering}

\begin{definition}[Positive discovery lineages]
\label{def:philosophy-positive-discovery-lineages}
A positive discovery lineage contains at least one positive discovery
transition. A pre-positive discovery lineage contains a certified
discovery step that is not yet positive. A delayed-positive lineage
becomes positive only after later ledger repair, compression, hardening,
transfer, or unification work. A transient-negative lineage has an
initial discovery step whose net information is negative.
\end{definition}

\begin{theorem}[Discovery can become positive later]
\label{thm:philosophy-discovery-can-become-positive-later}
A certified discovery transition with nonpositive net information can
become part of a positive discovery lineage after later audit work.
\end{theorem}
\begin{proof}
The initial classifier shift can impose high source, stability, ledger,
seal, semantic, or verification costs. Later work can lower debt, reduce
score, increase transfer, or improve unification. The total transition
from the original state to the later state can then have positive net
information.
\end{proof}

\begin{theorem}[Positive status can decay under new debt]
\label{thm:philosophy-positive-status-can-decay}
A positive discovery claim can lose positive status when later audit
reveals critical debt large enough to erase the positive margin.
\end{theorem}
\begin{proof}
Positive status depends on $\Delta\mathsf{Info}_{\mathbf w}>0$. Newly
recorded critical debt increases the debt term. If it exceeds the margin,
the inequality no longer holds.
\end{proof}

\begin{definition}[Discovery laundering]
\label{def:philosophy-discovery-laundering}
Scope laundering creates apparent positive gain by hiding a scope
narrowing. Debt laundering hides ledger, semantic, verification,
intervention, or generalization debt. Classifier laundering presents
feature-side, ledger-side, hardening-side, or semantic-side improvement
as classifier novelty.
\end{definition}

\begin{theorem}[Laundering invalidates positive discovery claims]
\label{thm:philosophy-laundering-invalidates-positive-discovery}
Any positive discovery claim that relies on scope, debt, or classifier
laundering is invalid.
\end{theorem}
\begin{proof}
Scope laundering changes the domain of the benefit and debt calculation
without sealing the change. Debt laundering suppresses terms subtracted
by net information. Classifier laundering asserts classifier novelty
where the classifier relation is unchanged. Each case violates a
necessary audit condition for positive discovery.
\end{proof}

\begin{theorem}[Positive interpretability discovery theorem]
\label{thm:philosophy-positive-interpretability-discovery-theorem}
Positive interpretability discovery is certified classifier novelty with
positive net explanation information under a public, debt-complete,
scope-sealed cost protocol.
\end{theorem}
\begin{proof}
\autoref{thm:philosophy-positive-discovery-implies-certified-discovery}
gives certified discovery, including classifier novelty, NameCert,
ledger, witness, and not-claimed boundary.
\autoref{def:philosophy-positive-discovery-transition} supplies the
strict net-information inequality.
\autoref{thm:philosophy-positive-discovery-requires-protocol-completeness}
and \autoref{cor:philosophy-positive-discovery-counts-critical-debts}
require a public protocol and critical debt accounting.
\autoref{thm:philosophy-laundering-invalidates-positive-discovery}
rules out apparent gains obtained by hiding scope, debt, or classifier
non-novelty. These conditions are exactly the stated characterization.
\end{proof}
