\chapter{A Concrete Naming Certificate for $\CauchyRealSpreadUp$}
\label{ch:concrete-instances-cauchy-real-spread-namecert}
\origin{human}

Following Bishop and Bridges on regular Cauchy real names and Brouwer-style spread presentations, the $\CauchyRealSpreadUp$ packet records the finite spread interface through which a countable family of regular Cauchy real-name windows is read without importing choice sequences or quotient reals. It sits after the prefix discipline of \autoref{ch:concrete-instances-brouwer-spread-namecert}, the finite window schedule of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a spread-indexed real-name boundary, not a completed branch, not a selected Cauchy representative, not countable choice, not quotient real equality, and not a completeness principle for $\RealUp$.

\begin{definition}[CauchyRealSpread carrier]
\label{def:cauchy-real-spread-carrier}
A $\CauchyRealSpreadUp$ carrier is a finite $\BHist$ packet
$$
S=(R,W,E,T,Q,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the spread root row inherited from $\BrouwerSpreadUp$, recording the displayed root prefix and its admitted prefix-tree boundary.
\item $W$ is the finite window row, listing the spread prefixes and request windows whose regular Cauchy real-name data may be inspected.
\item $E$ is the extension law row, requiring every displayed extension of an admitted prefix to remain inside the same spread discipline before any real-name read is public.
\item $T$ is the $\StreamNameUp$ row that schedules finite observations over the admitted prefixes.
\item $Q$ is the $\RegSeqRatUp$ row obtained from the scheduled windows and the $\DyadicRatCoreUp$ tolerance ledger.
\item $A$ is the terminal $\RealUp$ seal row, available only after the spread root, finite window, extension law, stream schedule, dyadic ledger, and regular rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the spread root, finite window, extension law, StreamName, RegSeqRat, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from spread-prefix admission through finite window inspection, extension-law checking, stream scheduling, regular rational readback, and Real sealing.
\item $P$ is the $\Pkg$ provenance over $\CauchyRealSpreadUp$, $\BrouwerSpreadUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyRealSpreadUp}$ row.
\end{enumerate}
The carrier has no coordinate for completed infinite branches, choice-sequence selection, quotient real equality, selected Cauchy representatives, host real equality, countable choice, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CauchyRealSpread NameCert obligations]
\label{thm:cauchy-real-spread-namecert-obligations}
For an accepted $\CauchyRealSpreadUp$ carrier $S=(R,W,E,T,Q,A,H,C,P,N)$, the local $\NameCert_{\CauchyRealSpreadUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the spread root, finite window, extension law, StreamName row, RegSeqRat row, Real seal, componentwise transport, continuation replay, provenance, and local naming rows;
\item root compatibility, requiring every public real-name request to start from the displayed $\BrouwerSpreadUp$ root row $R$;
\item window discipline, requiring the finite request window $W$ to be read before any stream, rational, or real-seal row is consumed;
\item extension stability, requiring each admitted prefix extension to pass through the law row $E$ before the scheduled stream row $T$ is public;
\item regular readback exactness, requiring every finite real-name observation to pass through the $\DyadicRatCoreUp$ tolerance ledger and the $\RegSeqRatUp$ row $Q$ before the $\RealUp$ seal $A$ is read;
\item transport and replay, requiring $H$ and $C$ to preserve the same ordered route under $\hsame$ transport and displayed $\Cont$ replay;
\item ledger non-escape, excluding completed branches, choice-sequence selection, quotient real equality, selected Cauchy representatives, host real equality, countable choice, and ambient completeness of $\RealUp$.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the accepted carrier. The tuple exposes exactly the spread root $R$, finite window $W$, extension law $E$, stream schedule $T$, regular rational readback $Q$, Real seal $A$, and structural rows $H,C,P,N$.

Root compatibility and window discipline follow from the tuple order. A public real-name request begins with the displayed $\BrouwerSpreadUp$ root and then reads only the finite windows stored in $W$.

Extension stability is recorded by $E$. The row checks each displayed prefix extension before the scheduled $\StreamNameUp$ observations in $T$ can be consumed, so no completed branch or choice-sequence selection is introduced.

Regular readback exactness then routes every tolerance request through the $\DyadicRatCoreUp$ ledger and the $\RegSeqRatUp$ row $Q$ before the terminal $\RealUp$ seal $A$ is available. The rows $H$ and $C$ transport and replay this same ordered route, while $P$ and $N$ record provenance and local naming.

Since the carrier has no further coordinate, quotient real equality, selected representatives, host real equality, countable choice, and ambient completeness of $\RealUp$ cannot be read from the packet.
\end{proof}

\closureat{CauchyRealSpreadUp}{seedStr}

\begin{closurestatus}{\CauchyRealSpreadUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-real-spread-carrier} and \autoref{thm:cauchy-real-spread-namecert-obligations} seed the spread-indexed regular Cauchy real-name surface through $\BrouwerSpreadUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim completed infinite branches, choice-sequence selection, quotient real equality, selected Cauchy representatives, host real equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, spread-root compatibility, finite-window discipline, extension stability, regular readback exactness, transport replay, provenance, and non-escape for BEDC.Derived.CauchyRealSpreadUp.}
  \constructivestory{A $\CauchyRealSpreadUp$ packet is generated from a BrouwerSpread root, finite request windows, an extension law, a StreamName schedule, DyadicRatCore tolerance data, RegSeqRat readback, a Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
