\begin{theorem}[Group singleton contextual triple continuation product-unit exact visibility]
\label{thm:group-singleton-contextual-triple-continuation-product-unit-exact-visibility}
For histories $L_0,R_0,L_1,R_1,P,Q,S,T,U,V,W,X,r:\mathsf{BHist}$, if
$A_{\emp}(L_0)$, $A_{\emp}(R_0)$, $A_{\emp}(L_1)$, $A_{\emp}(R_1)$,
$\ContR(P,Q,S)$, $\ContR(S,T,U)$, and $\ContR(U,V,W)$, then
$$
\begin{array}{c}
R_{\emp}(\mathsf{append}(\mathsf{append}(L_0,\mathsf{append}(W,X)),L_1),
\mathsf{append}(\mathsf{append}(R_0,\emp),R_1))\\
\Longleftrightarrow\\
\bigl(A_{\emp}(P)\land A_{\emp}(Q)\land A_{\emp}(T)\land A_{\emp}(V)\land
A_{\emp}(X)\bigr)\land
\bigl(\ContR(P,Q,\Ezero(r))\Rightarrow\mathsf{False}\bigr)\land
\bigl(\ContR(P,Q,\Eone(r))\Rightarrow\mathsf{False}\bigr)\land
\bigl(\ContR(S,T,\Ezero(r))\Rightarrow\mathsf{False}\bigr)\land
\bigl(\ContR(S,T,\Eone(r))\Rightarrow\mathsf{False}\bigr)\land
\bigl(\ContR(U,V,\Ezero(r))\Rightarrow\mathsf{False}\bigr)\land
\bigl(\ContR(U,V,\Eone(r))\Rightarrow\mathsf{False}\bigr).
\end{array}
$$
The ten-field fit is: traditional target terminal-group contextual three-step
continuation product-unit exact visibility; BEDC source concrete singleton
$\GroupUp$ over $\mathsf{BHist}$ plus two context pairs, three $\ContR$
witnesses, visible continuation endpoints, and append; carrier $A_{\emp}$;
classifier $R_{\emp}$; stability from two-sided context cancellation, triple
continuation product-unit coverage, terminal collapse, and terminal classifier
packaging; ledger the two hidden context pairs, three continuation witnesses,
suffix endpoint, and visible result seed $r$; core theorem list
\autoref{thm:group-singleton-classifier-two-sided-context-cancel} and
\autoref{thm:group-singleton-triple-continuation-product-unit-coverage-and-visibility};
exactness the displayed iff package; downstream consumer $\QuotientGroupUp$
path compression; and status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
For the forward direction, assume the displayed contextual classifier. Apply
\autoref{thm:group-singleton-classifier-two-sided-context-cancel} with
$Q=\mathsf{append}(W,X)$ and $S=\emp$ to the four context carrier witnesses.
This strips the hidden contexts and reduces the classifier to
$R_{\emp}(\mathsf{append}(W,X),\emp)$.

Apply
\autoref{thm:group-singleton-triple-continuation-product-unit-coverage-and-visibility}
to the three continuation witnesses. Its classifier direction supplies the
five carrier factors $A_{\emp}(P)$, $A_{\emp}(Q)$, $A_{\emp}(T)$,
$A_{\emp}(V)$, and $A_{\emp}(X)$; its visibility clause supplies the six
visible-result exclusions for the same endpoint seed $r$.

Conjoining these facts gives the full right-hand visible-classification
package. No extra hidden context data remains, because all four context
carriers were consumed by the cancellation step.

For the reverse direction, assume the right-hand package. Its carrier component
contains $A_{\emp}(P)\land A_{\emp}(Q)\land A_{\emp}(T)\land A_{\emp}(V)\land
A_{\emp}(X)$, which is exactly the carrier side of the triple continuation
product-unit coverage theorem.

Use the reverse classifier direction of
\autoref{thm:group-singleton-triple-continuation-product-unit-coverage-and-visibility}
with $\ContR(P,Q,S)$, $\ContR(S,T,U)$, and $\ContR(U,V,W)$ to reconstruct
$R_{\emp}(\mathsf{append}(W,X),\emp)$. The six exclusion clauses remain part
of the package but are not needed to rebuild this unwrapped classifier.

Finally apply the reverse direction of
\autoref{thm:group-singleton-classifier-two-sided-context-cancel} with the four
context carrier witnesses. This wraps the unwrapped classifier by the left and
right context pairs and gives the displayed contextual classifier.
\end{proof}
