\section{Center abelian normal package}
\label{sec:group-center-abelian-normal-package}

\begin{theorem}[Group center abelian normal subgroup package]
\label{thm:group-center-abelian-normal-subgroup-package}
For a BEDC history-level group operation $\mathsf{mul}$ over
$\mathsf{BHist}$ with associativity, left and right identity laws for $e$,
multiplication congruence, and two-sided inverse laws, the center carrier
$\mathsf{Z}(G)$ of \autoref{def:group-center-carrier} has all
normal-subgroup rows of \autoref{thm:group-center-normal-subgroup} and also
the abelian row
$$
\forall x,y:\mathsf{BHist},\quad
\mathsf{Z}(G)(x)\Rightarrow
\mathsf{Z}(G)(y)\Rightarrow
\hsame(\mathsf{mul}(x,y),\mathsf{mul}(y,x)).
$$
The ten-field fit is: traditional target center as an abelian normal subgroup;
BEDC source $\GroupUp$ over $\mathsf{BHist}$; carrier $\mathsf{Z}(G)$;
classifier $\hsame$; stability from the checked normal-subgroup theorem plus
center commutativity at each test history; ledger central endpoints $x,y$ and
the two product orders $\mathsf{mul}(x,y)$ and $\mathsf{mul}(y,x)$; core
theorem list \autoref{thm:group-center-normal-subgroup} and
\autoref{def:group-center-carrier}; exactness the displayed commutativity row
together with the normal-subgroup rows; standard bridge ordinary group center;
status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
The normal-subgroup part is exactly
\autoref{thm:group-center-normal-subgroup}. It supplies the unit, product,
inverse, classifier transport, conjugation, and centralizer-normalizer
inclusion rows for the carrier $\mathsf{Z}(G)$.

For the abelian row, fix $x,y:\mathsf{BHist}$ and assume
$\mathsf{Z}(G)(x)$ and $\mathsf{Z}(G)(y)$. Unfold
\autoref{def:group-center-carrier}. The witness $\mathsf{Z}(G)(x)$ is a
universal commutativity certificate against every test history, so applying it
to the test history $y$ gives
$$
\hsame(\mathsf{mul}(x,y),\mathsf{mul}(y,x)).
$$

The carrier witness for $y$ is part of the abelian normal-subgroup package
interface, and it is used by the product and inverse rows inherited from
\autoref{thm:group-center-normal-subgroup}. The displayed pointwise
commutativity itself only needs the center witness for $x$ at the chosen test
history $y$.
\end{proof}
\begin{theorem}[Group singleton public operation surface]
\label{thm:group-singleton-public-operation-surface}
For the concrete singleton history group instance of
\autoref{def:concrete-singleton-history-group-instance}, the public carrier is
$A_{\emp}$, multiplication is $\mathsf{append}$, unit is $\emp$, inverse is the
constant operation $h\mapsto\emp$, and the public classifier is $R_{\emp}$.
This surface is packaged by the following four clauses.
\begin{enumerate}
  \item Multiplication, unit, and inverse endpoints remain in the carrier
  $A_{\emp}$ and are classified by $R_{\emp}$ whenever their inputs are carried.

  \item Every public expression generated from carried endpoints by
  multiplication, unit, and inverse has readback classified with $\emp$.

  \item Left and right singleton append contexts preserve and reflect the
  public classifier by the existing append-context cancellation rows.

  \item The source, pattern, and ledger predicates expose only singleton
  carrier witnesses and append or inverse expression provenance. Hence the
  public surface admits no endpoint outside $A_{\emp}$.
\end{enumerate}
\end{theorem}
\begin{proof}
The carrier, classifier, multiplication, unit, and inverse are exactly the
objects named in \autoref{def:concrete-singleton-history-group-instance}.
Theorem~\ref{thm:group-singleton-history-semantic-namecert} packages them as
the singleton-history $\mathsf{SemanticNameCert}$ for $\GroupUp$, so the source
and classifier fields of the public surface are not additional data.

For the endpoint clauses, use
Theorem~\ref{thm:concrete-singleton-history-group-laws} together with the
singleton endpoint readback row recorded by
$\mathsf{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}$. Multiplication
closure carries $\mathsf{append}(h,k)$ from carried inputs; the unit row carries
$\emp$; inverse closure carries the constant inverse endpoint $\emp$; and the
readback row classifies each generated endpoint against $\emp$ by $R_{\emp}$.

Public expressions are built by induction on the expression tree. The base
case is a carried endpoint, whose singleton witness reads back to $\emp$. The
unit and inverse cases use the constant endpoint $\emp$. The multiplication
case applies multiplication closure to the two inducted carrier witnesses and
then composes their readback classifiers through the append law supplied by the
same checked singleton group rows.

For contextual visibility, apply
Theorem~\ref{thm:group-singleton-classifier-append-context-cancel} to the left
append contexts. The right-context row in the same singleton block gives the
corresponding suffix form, and the two-sided row combines the two orientations.
Thus wrapping a public endpoint by singleton append contexts neither creates
nor hides a classifier witness.

Finally, the no-hidden-leakage clause is just the exactness content of the
singleton certificate. Source predicates expose carrier witnesses
$A_{\emp}(h)$, pattern predicates expose only the empty endpoint and append
shape used by the generated expression, and ledger rows record the concrete
append or constant-inverse provenance. Any admitted public endpoint therefore
carries a witness to $A_{\emp}$, so no endpoint outside the singleton carrier
is admitted by this operation surface.
\end{proof}
\begin{theorem}[Group singleton acceptance bridge]
\label{thm:group-singleton-acceptance-bridge}
The public singleton surface of
\autoref{thm:group-singleton-public-operation-surface} supplies a paper-level
$\StdBridge(\GroupUp,T_{\mathbf{1}})$ to the terminal one-element group. The
encode map sends the unique host element to the carried BEDC endpoint $\emp$,
and the decode map sends every carried endpoint to the unique host element.
The two round trips are witnessed by $R_{\emp}$ and singleton carrier readback.
The theorem-preservation list is the finite list of terminal group rows:
unit, associativity, inverse, and cancellation, with BEDC counterparts collected
by $\mathsf{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}$. The no-host-leak
field holds because the public surface exposes only $\mathsf{BHist}$,
$A_{\emp}$, $R_{\emp}$, $\mathsf{append}$, $\emp$, and the constant inverse.
\end{theorem}
\begin{proof}
We check the six fields of \autoref{sec:acceptance-bridge-six-fields}. The
encode field is the constant map from the terminal host carrier to $\emp$.
The endpoint $\emp$ is public by
\autoref{thm:group-singleton-public-operation-surface}, so the map lands in
$A_{\emp}$ and respects the public classifier.

The decode field sends every carried BEDC endpoint to the unique element of
$T_{\mathbf{1}}$. Since the host carrier has one element, classifier-respect is
immediate on the host side: any two decoded carried endpoints are the same host
element.

For the decode-encode round trip, start with the unique host element, encode it
as $\emp$, and decode back to the unique host element. This is the terminal
group identity judgment.

For the encode-decode round trip, start with a carried endpoint $h:A_{\emp}$.
Decoding gives the unique host element, and encoding returns $\emp$. The
singleton carrier readback clause of
\autoref{thm:group-singleton-public-operation-surface} supplies
$R_{\emp}(h,\emp)$, which is exactly the BEDC classifier witness required for
this round trip.

The theorem-preservation field is finite. Its entries are the unit,
associativity, inverse, and cancellation rows of the terminal group, translated
to the BEDC singleton operation surface by the checked law package
$\mathsf{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}$. No other host
group theorem is claimed by this list.

Finally, the no-host-leak field follows from the public-object inventory in
\autoref{thm:group-singleton-public-operation-surface}. The bridge uses the
host terminal group only to name the unique decode value and the terminal
round-trip judgment. The BEDC-facing surface remains $\mathsf{BHist}$,
$A_{\emp}$, $R_{\emp}$, $\mathsf{append}$, $\emp$, and the constant inverse, so
no host primitive enters the exported $\GroupUp$ object.
\end{proof}
\begin{closurestatus}{\GroupUp}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{\autoref{thm:group-singleton-public-operation-surface} and \autoref{thm:group-singleton-acceptance-bridge} close the singleton carrier $A_{\emp}$, multiplication $\mathsf{append}$, unit $\emp$, constant inverse, classifier $R_{\emp}$, expression readback, no-hidden-leakage, and the paper-level bridge to $T_{\mathbf{1}}$.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}
  \bridgestatus{paperBridge}
  \notclaimed{Arbitrary groups, homomorphisms, subgroup lattices, quotient groups, non-singleton classifiers, and machine-checked bridge verification are not closed here.}
  \upgradepath{Mature closure requires broader examples or completeness statements beyond the terminal singleton bridge.}
\end{closurestatus}
