\begin{closurestatus}{\GroupUp}
  \constructivestory{The carrier of $\GroupUp$ at this closure level is the singleton history class containing only the empty history: a history $h$ is admitted when $h$ is history-equal to $\emp$. The classifier is history-equality restricted to this singleton, so the equivalence is trivial. The source spec is the same singleton predicate; the pattern spec records the multiplication (continuation of the carried element with itself returns the empty history), the unit (the empty history), and the inverse (the inverse of every carried element is again the empty history); the ledger keeps the visible singleton aligned with its raw counterpart. The five name-certificate obligations follow trivially because the carrier has exactly one inhabited equivalence class and history-equality is an equivalence. A history $h$ lies in the signature gap of a $\GroupUp$ token $p$ when the source-domain admits $h$, the signature relation pairs $h$ with an answer history and an evidence ledger, and the token-introduction relation maps that answer to $p$ --- collapsing to ``$h$ is history-equal to $\emp$ and $p$ is the singleton group element''. Beyond the in-paper certificate, the chapter pairs $\GroupUp$ with a singleton terminal standard bridge that confirms the singleton behaves as the trivial group $\{e\}$ in every external comparison. The chapter registers this singleton group construction under the name $\GroupUp$; the left and right inverse laws are unit-law calculations rather than new algebraic motion, no non-singleton group carrier or primitive inverse object is introduced, and full group theory waits for later closure levels.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{This chapter closes the concrete singleton-history group certificate: carrier, classifier, multiplication, unit, inverse, and the named law package are bound for the $\mathsf{BHist}$ singleton instance.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}
  \bridgestatus{bridgeChecked}
  \notclaimed{This record does not close a public group object surface, a standard bridge, or non-singleton group classifiers.}
  \upgradepath{No further upgrade -- chapter at top of formal axis.}
\end{closurestatus}
