\chapter{A Concrete Naming Certificate for $\DyadicCauchyOscillationModulusUp$}
\label{ch:concrete-instances-dyadic-cauchy-oscillation-modulus-namecert}
\origin{human}

Following Bishop and Bridges, the $\DyadicCauchyOscillationModulusUp$ packet records the finite modulus surface by which dyadic Cauchy oscillation reads are scheduled before a regular real completion route consumes them. It sits between the oscillation criterion of \autoref{ch:concrete-instances-cauchy-oscillation-criterion-namecert}, the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet also records compatibility with the explicit Cauchy modulus surface of \autoref{ch:concrete-instances-cauchymodulus-namecert}, while keeping completeness, quotient equality, selected limits, host equality, trichotomy, and choice outside the carrier.

\begin{definition}[Dyadic Cauchy oscillation modulus carrier]
\label{def:dyadic-cauchy-oscillation-modulus-carrier}
A $\DyadicCauchyOscillationModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(O,D,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the oscillation ledger, read through $\CauchyOscillationCriterionUp$ as the finite record saying which pair of tail observations is compared for a requested tolerance.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and modulus row, containing the requested dyadic radius, the displayed threshold, and the dyadic comparison budget used by $O$.
\item $W$ is the visible tail-window schedule in $\StreamNameUp$, listing the finite windows beyond the threshold supplied by $D$ and consumed by the oscillation read.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same windows and dyadic tolerance ledger.
\item $E$ is the $\RealUp$ seal row, visible only after $O,D,W,R$ have fixed the finite oscillation-modulus route.
\item $H$ stores componentwise $\hsame$ transport for $O,D,W,R,E,C,P,N$ and the local packet shape.
\item $C$ stores displayed $\Cont$ replay from a tolerance request to the dyadic threshold row, from that threshold to the visible tail windows, from the windows to the oscillation ledger, and from the ledger to the $\RegSeqRatUp$ and $\RealUp$ rows.
\item $P$ is the $\Pkg$ provenance over $\DyadicCauchyOscillationModulusUp$, $\CauchyOscillationCriterionUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicCauchyOscillationModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $O,D,W,R,E,H,C,P,N$. It has no coordinate for Real completeness, quotient stream equality, selected limits, host equality, trichotomy, countable choice, or an unbounded search over tails.
\end{definition}

\begin{theorem}[Dyadic Cauchy oscillation modulus route]
\label{thm:dyadic-cauchy-oscillation-modulus-route}
Every oscillation read exported by an accepted $\DyadicCauchyOscillationModulusUp$ carrier factors through
$$
D\longmapsto W\longmapsto O\longmapsto R\longmapsto E
$$
together with the displayed $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\DyadicCauchyOscillationModulusUp}$ row. Thus the read is a finite dyadic modulus packet for tail oscillation, not a Real-completeness principle, quotient stream equality, selected limit, host equality, trichotomy row, or countable-choice selector.
\end{theorem}
\begin{proof}
Project the accepted carrier in \autoref{def:dyadic-cauchy-oscillation-modulus-carrier}. The dyadic tolerance and modulus row $D$ is the only coordinate that supplies the requested radius and finite threshold.

The visible tail-window schedule $W$ is downstream of $D$. It displays the finite windows over which the oscillation ledger $O$ may compare tail reads, so $O$ cannot be consumed before the requested dyadic threshold and windows have been shown.

The rows $R$ and $E$ are downstream handoffs. They receive the same displayed windows and dyadic tolerance data after the oscillation ledger has fixed the tail comparison, and the structural rows $H,C,P,N$ only transport, replay, source, and name this route.

No carrier coordinate supplies completeness, quotient equality, selected limits, host equality, trichotomy, choice, or an unbounded tail search. Hence every exported oscillation read is exhausted by the displayed finite route.
\end{proof}

\falsifiablePrediction{Every $\RegSeqRatUp$ or $\RealUp$ consumer of a $\DyadicCauchyOscillationModulusUp$ packet must first display the dyadic tolerance and modulus row, the visible $\StreamNameUp$ tail windows, and the $\CauchyOscillationCriterionUp$ ledger before any readback or seal row is consumed.}

\independenceWitness{cauchyoscillationcriterion, cauchymodulus, dyadicratcore, streamname, regseqrat, real: $\DyadicCauchyOscillationModulusUp$ is not bijective to any listed sibling because it jointly carries an oscillation ledger, dyadic tolerance and modulus data, visible tail-window scheduling, regular rational readback, a real seal boundary, componentwise transport, continuation replay, provenance, and local naming.}

\closureat{DyadicCauchyOscillationModulusUp}{seedStr}

\begin{closurestatus}{\DyadicCauchyOscillationModulusUp}
  \constructivestory{A $\DyadicCauchyOscillationModulusUp$ packet is generated from an oscillation ledger, a DyadicRatCore tolerance and modulus row, visible StreamName tail windows, RegSeqRat readback, a RealUp seal row, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-cauchy-oscillation-modulus-carrier} and \autoref{thm:dyadic-cauchy-oscillation-modulus-route} seed the finite Bishop--Bridges dyadic modulus packet for Cauchy oscillation reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient stream equality, selected limits, host equality, trichotomy, countable choice, ambient real arithmetic, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic tolerance exactness, tail-window scheduling, oscillation ledger routing, regular rational handoff, real-seal handoff, transport, replay, provenance, and non-escape for BEDC.Derived.DyadicCauchyOscillationModulusUp.}
\end{closurestatus}
