\chapter{A Concrete Naming Certificate for $\FractionalSobolevUp$}
\label{ch:concrete-instances-fractional-sobolev-namecert}
\origin{human}

Following Adams and Fournier on fractional Sobolev and Slobodeckij spaces, the $\FractionalSobolevUp$ packet records the finite carrier surface by which a downstream analysis consumer reads non-integer smoothness without importing a completed quotient function space. It sits over the Sobolev weak-derivative surface of \autoref{ch:concrete-instances-sobolev-namecert}, the weak-derivative observation route of \autoref{ch:concrete-instances-weak-derivative-namecert}, the dyadic metric tolerance ledger of \autoref{ch:concrete-instances-dyadic-metric-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only finite difference windows, dyadic scales, seminorm ledgers, componentwise transport, replay, provenance, and local naming evidence.

\begin{definition}[Fractional Sobolev carrier]
\label{def:fractional-sobolev-carrier}
A $\FractionalSobolevUp$ carrier is a finite $\BHist$ packet
$$
F=(S,W,D,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SobolevUp$ source row naming the integer-order weak-derivative and magnitude surface already accepted by the consumer.
\item $W$ is the $\WeakDerivativeUp$ observation row used to anchor finite weak-test reads when the fractional packet is compared to the ordinary Sobolev surface.
\item $D$ is the $\DyadicMetricUp$ scale row naming the inspected dyadic radii, difference windows, and finite comparison thresholds.
\item $Q$ is the fractional-difference seminorm ledger, recorded as finite pairs of displayed source windows and dyadic scale requests.
\item $R$ is the $\RealUp$ readback row for the finite magnitude comparisons exposed by $Q$.
\item $E$ is the terminal exclusion row stating that the packet has no coordinate for quotient functions, almost-everywhere equality, completed measure spaces, Bessel-potential transforms, or host interpolation functors.
\item $H$ records componentwise $\hsame$ transport for the Sobolev source, weak-derivative row, dyadic metric scale row, seminorm ledger, real readback, exclusion row, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a fractional smoothness request through $S,W,D,Q,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FractionalSobolevUp$, $\SobolevUp$, $\WeakDerivativeUp$, $\DyadicMetricUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FractionalSobolevUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,W,D,Q,R,E,H,C,P,N$. It has no coordinate for a host fractional Sobolev quotient, a selected representative, a completed $L^p$ carrier, a Fourier transform, a Bessel-potential model, or an interpolation-space equality.
\end{definition}

\begin{theorem}[Fractional Sobolev NameCert obligation]
\label{thm:fractional-sobolev-namecert-obligation}
For every accepted $\FractionalSobolevUp$ carrier
$$
F=(S,W,D,Q,R,E,H,C,P,N),
$$
the local $\NameCert_{\FractionalSobolevUp}$ surface consists exactly of carrier admission for the $\SobolevUp$ source row, the $\WeakDerivativeUp$ observation row, the $\DyadicMetricUp$ scale row, the finite fractional-difference seminorm ledger, the $\RealUp$ magnitude readback, the exclusion row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. A consumer may use the packet as a finite non-integer smoothness certificate only after reading the displayed route
$$
\SobolevUp,\quad \WeakDerivativeUp,\quad \DyadicMetricUp,\quad \RealUp .
$$
The obligation exports no quotient function equality, no almost-everywhere representative, no completed measure carrier, no Fourier-side model, no Bessel-potential transform, and no host interpolation theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:fractional-sobolev-carrier}. The displayed rows are precisely the Sobolev source row, weak-derivative observation row, dyadic scale row, seminorm ledger, Real readback, exclusion row, and structural rows $H,C,P,N$.

The fractional read begins at $S$ and $W$, then reaches the finite dyadic windows in $D$ before the seminorm ledger $Q$ can be consumed. The readback row $R$ compares only the finite magnitude entries displayed by $Q$.

Transport and replay preserve that route componentwise through $H$ and $C$, while $P$ and $N$ source and name the same finite packet. Since the remaining analytic objects are absent from the carrier coordinates, they cannot be exported by the local NameCert surface.
\end{proof}

\falsifiablePrediction{An accepted $\FractionalSobolevUp$ read is refuted if it reaches a fractional smoothness consumer without displaying the same $\SobolevUp$ source row, $\WeakDerivativeUp$ observation row, $\DyadicMetricUp$ scale row, finite seminorm ledger, $\RealUp$ readback, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}

\independenceWitness{sobolev, weak-derivative, dyadic-metric, real: $\FractionalSobolevUp$ is not bijective to any listed sibling because it binds a Sobolev source, weak-test route, dyadic metric scale ledger, finite fractional-difference seminorm row, and Real readback as one non-integer smoothness packet.}

\closureat{FractionalSobolevUp}{seedStr}

\begin{closurestatus}{\FractionalSobolevUp}
  \constructivestory{A $\FractionalSobolevUp$ packet is generated from a Sobolev source row, a WeakDerivative observation row, a DyadicMetric scale row, a finite fractional-difference seminorm ledger, a RealUp magnitude readback, an exclusion row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fractional-sobolev-carrier} and \autoref{thm:fractional-sobolev-namecert-obligation} seed the finite non-integer smoothness route from Sobolev and weak-derivative data through dyadic metric scales to a RealUp readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient function equality, almost-everywhere representatives, completed measure carriers, Fourier-side models, Bessel-potential transforms, host interpolation theorems, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Sobolev source exactness, WeakDerivative observation routing, DyadicMetric scale nonescape, finite seminorm ledger exactness, RealUp readback nonescape, transport, replay, provenance, and local naming for BEDC.Derived.FractionalSobolevUp.}
\end{closurestatus}
