\chapter{A Concrete Naming Certificate for $\FiniteIntervalLatticeUp$}
\label{ch:concrete-instances-finite-interval-lattice-namecert}
\origin{human}

Following Bishop--Bridges constructive interval and net arguments, the $\FiniteIntervalLatticeUp$ packet records the finite lattice of dyadic interval cells that a real-and-completion consumer may inspect before it asks for limits, covers, or compact-window continuity. It sits after the dyadic rational arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the dyadic interval surface of \autoref{ch:concrete-instances-dyadicinterval-namecert}, the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the located interval carrier of \autoref{ch:concrete-instances-located-real-interval-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives L10 Real and Completion routes a visible finite meet-join substrate; it is not an ambient interval-domain completeness theorem, not an open-cover compactness principle, and not a quotient real equality row.

\begin{definition}[Finite interval lattice carrier]
\label{def:finite-interval-lattice-carrier}
A $\FiniteIntervalLatticeUp$ carrier is a finite $\BHist$ packet
$$
Q=(D,I,L,J,M,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ endpoint and radius ledger used by all interval cells.
\item $I$ is the finite list of $\DyadicIntervalUp$ cells with displayed lower and upper endpoints.
\item $L$ is the located-interval source row, read through \autoref{ch:concrete-instances-located-real-interval-namecert}.
\item $J$ is the finite join table: every listed pair of cells either has a displayed least containing cell or a displayed refusal row.
\item $M$ is the finite meet table: every listed pair of cells either has a displayed greatest common subcell or a displayed empty-intersection refusal row.
\item $S$ is the $\StreamNameUp$ window row that records which endpoint and cell observations are inspected.
\item $R$ is the $\RegSeqRatUp$ readback row reached from the displayed endpoint windows.
\item $E$ is the $\RealUp$ seal row exposed only after $D,I,L,J,M,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transports for all visible interval-lattice rows.
\item $C$ records displayed $\Cont$ replays from dyadic endpoint reads to lattice cells, meet-join tables, stream windows, regular readback, and Real sealing.
\item $P$ is the $\Pkg$ provenance over $\FiniteIntervalLatticeUp$, $\DyadicRatCoreUp$, $\DyadicIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedIntervalUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteIntervalLatticeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,I,L,J,M,S,R,E,H,C,P,N$. It has no coordinate for an infinite interval lattice, selected limit point, quotient real equality, open-cover compactness theorem, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Finite interval lattice NameCert obligations]
\label{thm:finite-interval-lattice-namecert-obligations}
For every accepted $\FiniteIntervalLatticeUp$ carrier
$$
Q=(D,I,L,J,M,S,R,E,H,C,P,N),
$$
the local $\NameCert_{\FiniteIntervalLatticeUp}$ surface consists exactly of carrier admission, dyadic endpoint ledger exposure, finite dyadic interval cell exposure, located-interval source exposure, finite join and meet tables, stream-window inspection, regular rational readback, Real seal nonescape, componentwise transport, continuation replay, provenance, and local naming. Every consumer of the lattice must read the displayed rows before using it in dyadic-net, located-interval, compact-window, or continuity arguments.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:finite-interval-lattice-carrier}. The packet exposes a finite tuple of dyadic endpoint rows, interval cells, located interval data, meet-join tables, window rows, readback rows, seal rows, transport, replay, provenance, and local naming.

The lattice operations are finite because $J$ and $M$ are displayed tables over the listed cells $I$. A consumer may inspect only the table entry or refusal row already stored in the packet, and the dyadic endpoint ledger $D$ supplies the comparisons used by those entries.

The analytic handoff then passes through $S$, $R$, and $E$. The stream row records finite endpoint observations, the regular rational row records the accepted readback from those windows, and the Real row seals the same route without adding a selected limit, quotient equality, or ambient completeness coordinate.

Finally, $H$, $C$, $P$, and $N$ preserve the displayed rows as BEDC certificate data. Thus every obligation is discharged through finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and no host interval lattice or open-cover compactness theorem can enter the local surface.
\end{proof}

\closureat{FiniteIntervalLatticeUp}{seedStr}

\begin{closurestatus}{\FiniteIntervalLatticeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-interval-lattice-carrier} and \autoref{thm:finite-interval-lattice-namecert-obligations} seed the finite dyadic interval lattice boundary for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close infinite interval-domain completeness, open-cover compactness, selected limits, quotient real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, meet-join table exactness, dyadic endpoint transport, RegSeqRat readback handoff, RealUp seal nonescape, and consumer-boundary proofs for BEDC.Derived.FiniteIntervalLatticeUp.}
  \constructivestory{A $\FiniteIntervalLatticeUp$ packet is generated from dyadic endpoint rows, finite dyadic interval cells, located interval source rows, finite meet and join tables, stream windows, regular rational readback, Real seal, componentwise transport, continuation replay, provenance, and a local NameCert row.}
\end{closurestatus}
