\chapter{A Concrete Naming Certificate for $\CauchyCompletionIdempotentUp$}
\label{ch:concrete-instances-cauchy-completion-idempotent-namecert}
\origin{human}

Following Bishop and Bridges constructive completion and the Bourbaki--Kelley language of completion as a reflective boundary, the $\CauchyCompletionIdempotentUp$ packet records the finite BEDC certificate that a second read of the L10 completion route contributes no new public completion object. It ties the monadic completion route of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, the unit packet of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the counit packet of \autoref{ch:concrete-instances-cauchy-completion-counit-namecert}, and the adjunction packet of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert} to the Real-and-Completion consumers of \autoref{ch:concrete-instances-real-cauchy-completion-namecert} and \autoref{ch:concrete-instances-uniformcompletion-namecert}. The chapter is only the finite reflective-idempotence surface for repeated completion reads; it does not add a quotient completion, a selected representative, ambient completeness, host real equality, countable choice, or bridge-axis evidence.

\begin{definition}[CauchyCompletionIdempotent carrier]
\label{def:cauchy-completion-idempotent-carrier}
A $\CauchyCompletionIdempotentUp$ carrier is a finite $\BHist$ packet
$$
I=(C_0,C_1,U,V,A,E,H,R,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $C_0$ is the first completion seal reached by the displayed L10 route through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$.
\item $C_1$ is the second completion seal obtained by applying the same completion read to $C_0$ as a completion-facing source.
\item $U$ is the $\CauchyCompletionUnitUp$ row that records the first admission into the completion-facing surface.
\item $V$ is the $\CauchyCompletionCounitUp$ row that returns an already displayed completion-facing read to the terminal real-seal route.
\item $A$ is the $\CauchyCompletionAdjunctionUp$ universal-property row that identifies the repeated completion read as a consumer of the same reflected route.
\item $E$ is the same-route classifier comparing the public reads of $C_0$ and $C_1$ through $U,V,A$.
\item $H$ records componentwise $\hsame$ transport for the two completion seals, the unit row, the counit row, the adjunction row, and the classifier row.
\item $R$ records displayed $\Cont$ replay for Real-and-Completion consumers that inspect either completion seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionIdempotentUp$, $\CauchyCompletionMonadUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionCounitUp$, $\CauchyCompletionAdjunctionUp$, $\RealCauchyCompletionUp$, $\UniformCompletionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionIdempotentUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient-completion equality, a selected completion representative, a host completed metric space, host real equality, countable choice, ambient completeness, or bridge-axis evidence.
\end{definition}

\begin{theorem}[CauchyCompletionIdempotent NameCert obligations]
\label{thm:cauchy-completion-idempotent-namecert-obligations}
For an accepted $\CauchyCompletionIdempotentUp$ carrier $I=(C_0,C_1,U,V,A,E,H,R,P,N)$, the local $\NameCert_{\CauchyCompletionIdempotentUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the two completion seals, unit row, counit row, adjunction row, same-route classifier, componentwise transport, displayed replay, provenance, and local naming rows;
\item unit/counit visibility, requiring every public read of the first and second completion seals to pass through the displayed $U$ and $V$ rows before reaching the terminal $\RealUp$ seal route;
\item double-completion route comparison, requiring the classifier $E$ to compare $C_0$ and $C_1$ only by the route displayed through $U,V,A$;
\item classifier transport, requiring transported packets with the same displayed rows to be identified by the carried $\hsame$ and $\Cont$ evidence;
\item ledger non-escape, stating that no quotient completion, selected representative, ambient completeness, host real equality, countable-choice schedule, or bridge-axis witness is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-idempotent-carrier}. The tuple lists exactly the first completion seal, second completion seal, unit row, counit row, adjunction row, same-route classifier, transport, replay, provenance, and local naming row.

Unit/counit visibility is read from $U$ and $V$. The first seal $C_0$ is admitted by the unit row, while the second seal $C_1$ can be returned to the same terminal route only through the counit row.

The route comparison is then forced by $A$ and $E$. The adjunction row supplies the universal-property boundary for completion-facing consumers, and the classifier row compares the two completion reads only after both are presented through the displayed unit/counit route.

Classifier transport is componentwise transport along $H$ followed by replay through $R$. Since the carrier is exhausted by $C_0,C_1,U,V,A,E,H,R,P,N$, the excluded quotient, representative-choice, host-equality, countable-choice, ambient-completeness, and bridge-axis data have no row from which a consumer could read them.
\end{proof}

\begin{theorem}[CauchyCompletionIdempotent Real completion handoff]
\label{thm:cauchy-completion-idempotent-real-completion-handoff}
Let $I=(C_0,C_1,U,V,A,E,H,R,P,N)$ be an accepted $\CauchyCompletionIdempotentUp$ carrier. Every $\RealCauchyCompletionUp$, $\UniformCompletionUp$, or $\RealUp$ consumer of the double-completion packet factors through the displayed L10 completion route
$$
C_0,C_1\longmapsto U,V,A\longmapsto E\longmapsto(H,R,P,N).
$$
The consumer receives only the finite rows of this route. It receives no quotient completion, selected representative, ambient completeness, host real equality, countable choice, or bridge-axis evidence.
\end{theorem}
\begin{proof}
Start with a Real-and-Completion consumer request for the double-completion packet. The carrier exposes the two completion seals only as $C_0$ and $C_1$, together with the rows that explain how they were admitted and returned through the same completion route.

The rows $U$ and $V$ force the consumer through the unit/counit boundary before any terminal seal can be inspected. The row $A$ supplies the adjunction-facing route by which a repeated completion read is consumed by the same reflective surface.

The classifier $E$ compares the two public reads only after that route has been displayed. Transport by $H$ and replay by $R$ preserve the same route for equivalent packets, while $P$ and $N$ record the provenance and local certificate.

No further field exists in $I$. Hence every $\RealCauchyCompletionUp$, $\UniformCompletionUp$, and $\RealUp$ consumer receives exactly the displayed L10 route and cannot obtain quotient completion data, a selected representative, ambient completeness, host real equality, countable choice, or bridge-axis evidence.
\end{proof}

\begin{closurestatus}{\CauchyCompletionIdempotentUp}
  \constructivestory{A $\CauchyCompletionIdempotentUp$ packet is generated from first and second completion seals, CauchyCompletionUnit and CauchyCompletionCounit rows, a CauchyCompletionAdjunction universal-property row, a same-route classifier, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-idempotent-carrier}, \autoref{thm:cauchy-completion-idempotent-namecert-obligations}, and \autoref{thm:cauchy-completion-idempotent-real-completion-handoff} seed the finite reflective-idempotence surface for repeated L10 completion reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, ambient completeness, host real equality, countable choice, public bridge evidence, or completeness of $\RealUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, unit/counit visibility, double-completion route comparison, classifier transport, Real-and-Completion handoff, and ledger non-escape for the same packet.}
\end{closurestatus}
