\begin{theorem}[$\ZNormalUp$ total-host terminal fuel determinacy]
\label{thm:znormal-total-host-terminal-fuel-determinacy}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the total-host terminal-fuel read is determined by the displayed typed endpoint row $T$, finite fuel row $F$, terminal-normality row $V$, and terminal read row $R$, transported only by $H$, replayed only by $C$, packaged only by $P$, and named only by $N$. The sibling normal-word row $K$ is read as finite ZeckendorfNormal and ZCarry evidence and cannot be replaced by host conversion, quotient computation, unrestricted evaluation, divergence oracle, or global normalizer data.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_total\_host\_terminal\_fuel\_determinacy}
\begin{proof}
Project the carrier from \autoref{def:znormal-carrier}. It exposes $T,F,V,K,R,H,C,P,N$ as the whole accepted packet, so terminal fuel has no second host-side coordinate.

Use \autoref{thm:znormal-root-terminal-carrier-admission} and \autoref{thm:znormal-root-terminal-nonescape-interface}. They bind terminal use to $T,F,V,R$ and keep the route inside the finite packet before any total-host consumer can read it.

Finally apply \autoref{thm:znormal-root-sibling-normalword-consumption} and \autoref{thm:znormal-root-total-host-refusal}. The $K$ row remains finite sibling normal-word evidence, while the refusal ledger excludes host conversion, quotient computation, unrestricted evaluation, divergence, and global normalization.
\end{proof}

\begin{theorem}[$\ZNormalUp$ downstream normal route exhaustion]
\label{thm:znormal-downstream-normal-route-exhaustion}
Every downstream normal-form route out of an accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N)
$$
is exhausted by terminal fuel through $T,F,V,R$, sibling normal-word evidence through $K$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local $\NameCert_{\ZNormalUp}$ naming through $N$. No downstream normal route may pass through host conversion, quotient computation, unrestricted evaluation, divergence oracle, or global normalizer rows.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:znormal-root-downstream-totality}. It places every downstream normal-form consumer inside the displayed root packet and gives no separate normal-output coordinate.

Apply \autoref{thm:znormal-total-host-terminal-fuel-determinacy}. Terminal fuel and terminal readback are determined by $T,F,V,R$ and the structural rows $H,C,P,N$.

For the sibling route, use \autoref{thm:znormal-root-sibling-normalword-consumption}. The row $K$ is consumed only through finite ZeckendorfNormal, ZCarry, and ContinuationTraceNormalForm surfaces. The total-host refusal theorem \autoref{thm:znormal-root-total-host-refusal} then removes host conversion, quotient computation, unrestricted evaluation, divergence, and global normalization from the downstream boundary.
\end{proof}

\begin{theorem}[$\ZNormalUp$ finite normal-word classifier compatibility]
\label{thm:znormal-finite-normalword-classifier-compatibility}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the finite normal-word classifier seen by a downstream consumer is compatible with the terminal route: $K$ may be consumed only after the typed endpoint $T$, finite fuel $F$, terminal-normality row $V$, terminal read $R$, $\hsame$ transport $H$, $\Cont$ replay $C$, package row $P$, and local $\NameCert_{\ZNormalUp}$ row $N$ have fixed the same packet. This compatibility exports no host conversion, quotient computation, unrestricted evaluator, divergence oracle, or global normalizer.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacketFiniteNormalwordClassifierCompatibility}
\begin{proof}
Start from \autoref{thm:znormal-root-normal-word-route-totality}. It identifies $K$ as the finite normal-word route through the ZeckendorfNormal and ZCarry sibling surfaces rather than a host computation.

Use \autoref{thm:znormal-root-normal-word-route-exposure} to attach that classifier route to $T,F,V,R,H,C,P,N$. The normal-word row cannot be detached from the terminal packet or read through an independent quotient computation.

Finally invoke \autoref{thm:znormal-downstream-normal-route-exhaustion}. Since every downstream normal route is already exhausted by the displayed packet and finite sibling surfaces, classifier compatibility contributes no route to host conversion, unrestricted evaluation, divergence detection, or global normalization.
\end{proof}

\begin{theorem}[$\ZNormalUp$ downstream ZCarry dependency route]
\label{thm:znormal-downstream-normal-route-zcarry-dependency}
Every downstream normal-form read of an accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N)
$$
consumes the normal-word row $K$ through \autoref{ch:concrete-instances-zeckendorf-normal-namecert} and \autoref{ch:concrete-instances-zcarry-namecert} before any terminal readback through $R,H,C,P,N$. The read therefore reaches ZeckendorfNormal and ZCarry sibling evidence as finite BEDC rows, not as host conversion, quotient normalization, unrestricted evaluation, divergence detection, or global normalization.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:znormal-downstream-normal-route-exhaustion}. It says that every downstream normal-form route is already exhausted by $T,F,V,K,R,H,C,P,N$ and that the row $K$ is the sibling normal-word route.

Next apply \autoref{thm:znormal-finite-normalword-classifier-compatibility}. The classifier compatibility theorem forces $K$ to remain attached to the same terminal packet before any downstream consumer reads $R,H,C,P,N$.

The two sibling labels name the concrete finite sources for that row. Thus $K$ is consumed through the ZeckendorfNormal and ZCarry chapters first, and the terminal readback can only replay the already displayed route.
\end{proof}

\begin{theorem}[$\ZNormalUp$ candidate-normal endpoint readback]
\label{thm:znormal-candidate-normal-endpoint-readback}
Every candidate-mediated normal endpoint consumer of an accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N)
$$
must read terminal fuel through $T,F,V,R$, finite normal-word evidence through $K$, and structural rows $H,C,P,N$ before it can feed a MetaCIC candidate-normalization or closed-normal consistency route. The endpoint readback exports no host conversion, quotient computation, unrestricted evaluator, divergence oracle, or global normalizer.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacketCandidateNormalEndpointReadback}
\begin{proof}
Apply \autoref{thm:znormal-total-host-terminal-fuel-determinacy}. It binds the terminal fuel and terminal readback rows to $T,F,V,R$ before any total-host endpoint can consume the accepted packet.

Next use \autoref{thm:znormal-downstream-normal-route-exhaustion}. Every downstream normal route is already exhausted by $T,F,V,R,K,H,C,P,N$, so a candidate-mediated endpoint has no independent host conversion or global-normalizer coordinate.

Finally invoke \autoref{thm:znormal-finite-normalword-classifier-compatibility}. The finite normal-word row $K$ is compatible with the same terminal route and must be read after the structural rows have fixed the packet. The downstream MetaCIC candidate-normalization consumer is therefore a later formalization site for this readback boundary, not a proof of unrestricted normalization.
\end{proof}
