\begin{theorem}[$\ZNormalUp$ terminal normality admission]
\label{thm:znormal-terminal-normality-admission}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the terminal-normality row $V$ is exposed only after the typed endpoint row
$T$ and the finite fuel row $F$ have already been displayed. The admission
surface therefore reads terminal normality as a finite packet coordinate, not
as a host conversion, quotient computation, unrestricted evaluator, divergence
oracle, or substrate halting theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:znormal-carrier}. The accepted packet is
the tuple $T,F,V,K,R,H,C,P,N$, and $V$ appears in that tuple after the typed
endpoint and fuel rows.

Apply \autoref{thm:znormal-namecert-obligations}. The local
$\NameCert_{\ZNormalUp}$ surface reads carrier admission, typed endpoint,
finite fuel, terminal normality, sibling normal-word evidence, terminal
readback, transport, replay, provenance, and naming as one finite certificate.

Use \autoref{thm:znormal-terminal-readback-exactness}. Terminal readback
factors through $T,F,V,R,H,C,P,N$, so the consumer can reach $V$ only through
the displayed endpoint and fuel path.

Finally apply \autoref{thm:znormal-finite-host-boundary-refusal}. The admitted
terminal-normality row remains inside the finite packet boundary and cannot be
reinterpreted as host conversion, quotient computation, unrestricted
evaluation, divergence detection, or a substrate halting theorem.
\end{proof}

\begin{theorem}[$\ZNormalUp$ finite-fuel classifier stability]
\label{thm:znormal-finite-fuel-classifier-stability}
For an accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
componentwise $\hsame$ transport preserves the finite fuel row $F$, terminal
normality row $V$, sibling normal-word row $K$, continuation readback row $R$,
continuation replay row $C$, provenance row $P$, and local naming row $N$.
The transported classifier surface adds no host conversion row and performs no
quotient computation.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_finite\_fuel\_classifier\_stability}
\begin{proof}
Start with \autoref{def:znormal-carrier}. The rows $F,V,K,R,H,C,P,N$ are
coordinates of the same displayed $\BHist$ packet, with $H$ reserved for
componentwise $\hsame$ transport.

Apply \autoref{thm:znormal-namecert-obligations}. The NameCert surface binds
finite fuel, terminal normality, sibling normal-word evidence, continuation
readback, transport, replay, provenance, and local naming to the same local
packet.

Use \autoref{thm:znormal-terminal-readback-exactness} for the continuation
side. The terminal read is transported through the listed finite rows and does
not introduce a separate evaluator.

Then apply \autoref{thm:znormal-finite-host-boundary-refusal}. Since the
boundary refuses host conversion and quotient computation, componentwise
$\hsame$ transport can preserve the displayed classifier rows only as finite
packet data.
\end{proof}

\begin{theorem}[$\ZNormalUp$ total-host ledger nonescape]
\label{thm:znormal-total-host-ledger-nonescape}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the total-host ledger exports exactly the finite terminal-normality, fuel,
normal-word, continuation, transport, replay, provenance, and local naming
rows displayed by the packet. It exports no divergence oracle, unrestricted
evaluator, global normalizer, host conversion row, or substrate halting
theorem.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_total\_host\_ledger\_nonescape}
\begin{proof}
Project the carrier by \autoref{def:znormal-carrier}. The ledger-readable
surface is the finite tuple $T,F,V,K,R,H,C,P,N$ and has no additional
total-host coordinate.

Apply \autoref{thm:znormal-namecert-obligations}. The same rows are read as
the local $\NameCert_{\ZNormalUp}$ obligations: endpoint, fuel, terminal
normality, sibling normal-word evidence, terminal readback, transport, replay,
provenance, and naming.

Use \autoref{thm:znormal-terminal-readback-exactness} to route any terminal
ledger read through the finite readback coordinates. The row $R$ is a
displayed continuation read, not an unrestricted evaluator.

Finally apply \autoref{thm:znormal-finite-host-boundary-refusal}. The
total-host ledger therefore cannot export divergence detection, global
normalization, host conversion, quotient computation, or a substrate halting
theorem.
\end{proof}
