\begin{theorem}[$\ZNormalUp$ terminal-route field exhaustion]
\label{thm:znormal-terminal-route-field-exhaustion}
Every terminal-route consumer of an accepted $\ZNormalUp$ packet must read the
finite terminal-normality row, finite fuel row, transport row, provenance row,
and local $\NameCert$ row from the displayed packet
$$
Z=(T,F,V,K,R,H,C,P,N).
$$
The route may use the terminal continuation row $R$ and displayed replay row
$C$, but it cannot replace the finite terminal packet by host conversion,
quotient normalization, unrestricted evaluation, divergence detection, or a
global normalizer.
\end{theorem}
\begin{proof}
Start with \autoref{thm:znormal-root-terminal-carrier-admission}. It displays
$T,F,V,K,R,H,C,P,N$ as the complete root terminal carrier and leaves no host
conversion or quotient-normalization coordinate.

Use \autoref{thm:znormal-root-total-host-source} to keep every total-host
source read inside the same finite packet. The source route therefore reaches
terminal normality only through the typed endpoint, fuel, continuation,
transport, replay, provenance, and naming rows already present.

Finally apply \autoref{thm:znormal-terminal-fuel-row-exhaustion}. It exhausts
terminal-normality consumers by $T,F,V,R,H,C,P,N$, with $K$ available only as
finite sibling normal-word evidence.
\end{proof}

\begin{theorem}[$\ZNormalUp$ normal-word sibling bridge]
\label{thm:znormal-normal-word-sibling-bridge}
The normal-word route of an accepted $\ZNormalUp$ packet is mediated by the
ZeckendorfNormal, ZCarry, TypedReductionNormalForm, and
ContinuationTraceNormalForm sibling surfaces already displayed by the packet.
The row $K$ is therefore a finite sibling normal-word row transported with
$T,F,V,R,H,C,P,N$, not a host normalizer, quotient conversion, divergence
oracle, or unrestricted evaluator.
\end{theorem}
\begin{proof}
Apply \autoref{thm:znormal-normal-word-sibling-exactness}. It identifies the
normal-word row $K$ with the finite Zeckendorf and carry-facing sibling routes
and keeps that row attached to the continuation readback surface.

Next use \autoref{thm:znormal-root-terminal-carrier-admission}. The typed
endpoint, fuel, terminal-normality, continuation, transport, replay,
provenance, and naming rows are displayed in the same root carrier, so the
sibling normal-word route cannot detach from the terminal packet.

Finally apply \autoref{thm:znormal-root-total-host-source}. The total-host
source is one finite packet, which rules out any separate host normalizer,
quotient conversion, divergence oracle, or unrestricted evaluator behind the
sibling bridge.
\end{proof}

\begin{theorem}[$\ZNormalUp$ total-host refusal readback]
\label{thm:znormal-total-host-refusal-readback}
The same accepted $\ZNormalUp$ packet that exposes the terminal route refuses
readback of divergence, host conversion, quotient normalization,
unrestricted evaluation, and global normalization. All terminal and
normal-word reads remain inside
$$
T,F,V,K,R,H,C,P,N,
$$
with no total-host row outside the finite packet.
\end{theorem}
\begin{proof}
First combine \autoref{thm:znormal-terminal-route-field-exhaustion} with
\autoref{thm:znormal-normal-word-sibling-bridge}. Terminal and normal-word
consumers are both confined to the displayed packet and its finite sibling
routes.

Use \autoref{thm:znormal-root-total-host-source}. It states that the total-host
source is the single finite packet, not a separately readable host conversion
or divergence object.

Finally apply \autoref{thm:znormal-terminal-fuel-row-exhaustion} and
\autoref{thm:znormal-normal-word-sibling-exactness}. These rows account for
all admitted terminal and sibling reads, leaving no coordinate for the refused
total-host readbacks.
\end{proof}
