\begin{theorem}[$\ZNormalUp$ total-host terminal carrier admission]
\label{thm:znormal-total-host-terminal-carrier-admission}
Every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N)
$$
admits a total-host terminal carrier only through the displayed terminal normality row $V$, bounded fuel replay row $F$, typed endpoint row $T$, and terminal continuation row $R$. The TasteGate-facing structural rows $H,C,P,N$ transport, replay, package, and name this same carrier, while $K$ remains finite sibling normal-word evidence. The carrier admits no host conversion row, quotient normalization row, unrestricted evaluator, divergence oracle, or global normalizer.
\end{theorem}
\begin{proof}
Project the carrier and its local obligations, \autoref{def:znormal-carrier} and \autoref{thm:znormal-namecert-obligations}. They expose exactly $T,F,V,K,R,H,C,P,N$ as the finite packet and make terminal normality a displayed row rather than a host-side conversion judgment.

Use the root terminal carrier and terminal non-escape surfaces, \autoref{thm:znormal-root-terminal-carrier-admission} and \autoref{thm:znormal-root-terminal-nonescape-interface}. These place terminal use on $T,F,V,R$ and keep the sibling normal-word row $K$ inside the same accepted packet.

Finally apply the TasteGate scope binding, \autoref{thm:znormal-tastegate-scope-binding}. The later TasteGate consumer sees the same finite field surface, so the admitted carrier cannot acquire any excluded host, quotient, evaluator, divergence, or global-normalization row.
\end{proof}

\begin{theorem}[$\ZNormalUp$ fuel readback TasteGate route]
\label{thm:znormal-fuel-readback-tastegate-route}
For every accepted $\ZNormalUp$ packet, the bounded fuel readback route reaches TasteGate only after the typed endpoint $T$, finite fuel $F$, terminal normality $V$, continuation readback $R$, and structural rows $H,C,P,N$ have been displayed. The normal-word row $K$ may contribute only the finite Zeckendorf and carry-facing sibling route. This TasteGate route exports no host conversion, quotient computation, unrestricted evaluation, divergence detection, or global normalization.
\end{theorem}
\begin{proof}
Start from terminal fuel field scope and terminal fuel row exhaustion, \autoref{thm:znormal-terminal-fuel-field-scope} and \autoref{thm:znormal-terminal-fuel-row-exhaustion}. They route fuel readback through $T,F,V,R,H,C,P,N$ and leave $K$ as finite sibling evidence.

Next use the root TasteGate field surface, \autoref{thm:znormal-root-tastegate-field-surface}. It identifies the TasteGate-facing consumer surface with the displayed tuple $T,F,V,K,R,H,C,P,N$.

The total-host refusal package, \autoref{thm:znormal-total-host-refusal-package}, closes the route. Since every excluded host or quotient object is absent from the packet, the fuel readback reaches TasteGate only through the displayed finite rows.
\end{proof}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalFuelReadbackTasteGateRoute}

\begin{theorem}[$\ZNormalUp$ downstream normal consumer non-escape]
\label{thm:znormal-downstream-normal-consumer-nonescape}
Every downstream normal-form consumer of an accepted $\ZNormalUp$ total-host packet is confined to terminal normality through $T,F,V,R$, finite sibling normal-word evidence through $K$, and the TasteGate-aligned structural rows $H,C,P,N$. The downstream route is exhausted by the displayed packet and cannot escape to host conversion, quotient normalization, unrestricted evaluation, divergence detection, substrate halting, or global normalization.
\end{theorem}
\begin{proof}
Begin with downstream normal route exhaustion, \autoref{thm:znormal-downstream-normal-route-exhaustion}. It accounts for terminal fuel, sibling normal-word evidence, componentwise transport, continuation replay, provenance, and local naming for every downstream normal-form consumer.

Apply the total-host terminal carrier admission above. The downstream consumer therefore reads the same terminal carrier that already passed through terminal normality, bounded fuel replay, TasteGate alignment, and the local structural rows.

Finally use the root total-host refusal theorem, \autoref{thm:znormal-root-total-host-refusal}. It refuses host conversion, quotient normalization, unrestricted evaluation, divergence detection, substrate halting, and global normalization for every route not carried by $T,F,V,K,R,H,C,P,N$. Hence the downstream normal consumer has no escape route beyond the displayed packet.
\end{proof}
