\begin{theorem}[ZNormal root fuel obligation surface]
\label{thm:znormal-root-fuel-obligation-surface}
Every accepted $\ZNormalUp$ packet exposes a finite root-fuel obligation
surface consisting of the finite fuel row, typed endpoint row,
Zeckendorf/carry comparison row, continuation terminal-read row, componentwise
transport row, displayed continuation row, package provenance row, and local
$\NameCert_{\ZNormalUp}$ row. A root-facing read of terminal normality must
pass through those rows before it can use the packet as normal-form evidence.
\end{theorem}
\begin{proof}
Start with the carrier definition and the local NameCert obligations of
\autoref{def:znormal-carrier} and \autoref{thm:znormal-namecert-obligations}.
They place typed endpoint readback, finite fuel, terminal normality, sibling
normal-word evidence, continuation terminal read, transport, replay,
provenance, and local naming in one accepted packet.

Next apply \autoref{thm:znormal-carry-normalization-obligation} and
\autoref{thm:znormal-continuation-terminal-route}. The sibling normal-word row
is read through the finite Zeckendorf and carry-facing comparison route, while
the continuation row is read only after the typed endpoint, fuel, and terminal
normality rows.

Finally use \autoref{thm:znormal-route-transport} and
\autoref{thm:znormal-root-namecert-readiness}. These bind the route through
$H,C,P,N$, so the root-fuel obligation surface is exactly the finite packet
displayed by the carrier and its local NameCert row.
\end{proof}

\begin{theorem}[ZNormal normal-form consumer readiness]
\label{thm:znormal-normal-form-consumer-readiness}
Every downstream normal-form consumer of an accepted $\ZNormalUp$ packet reads
terminal normality only through the finite fuel, typed endpoint,
Zeckendorf/carry comparison, continuation terminal-read, componentwise
transport, displayed continuation, package provenance, and local NameCert rows
of \autoref{thm:znormal-root-fuel-obligation-surface}. The consumer receives no
separate host conversion row, quotient computation, divergence oracle, or
global normalization procedure.
\end{theorem}
\begin{proof}
First apply \autoref{thm:znormal-root-fuel-obligation-surface}. It supplies the
finite route through which terminal normality is exposed to root-facing reads.

Next use \autoref{thm:znormal-root-normal-form-consumer-exhaustion} and
\autoref{thm:znormal-terminal-consumer-totality}. These force downstream
normal-form consumers to read the displayed root packet, not an external
normalizer or host-side evaluation object.

Finally combine \autoref{thm:znormal-fuel-normality-nonescape} with
\autoref{thm:znormal-root-unblock-nonescape-ledger}. The non-escape boundary
excludes host conversion, quotient computation, divergence, unrestricted
evaluation, and global normalization from the consumer interface. Thus
consumer readiness is exactly readiness to replay the finite fuel route.
\end{proof}

\begin{theorem}[ZNormal fuel route nonescape]
\label{thm:znormal-fuel-route-nonescape}
The root-fuel readiness route of an accepted $\ZNormalUp$ packet exports no
divergence oracle, host conversion, quotient computation, unrestricted
evaluator, or global normalization coordinate. Its public boundary is exhausted
by finite fuel, terminal normality, sibling Zeckendorf/carry comparison,
continuation terminal read, $\BHist$, componentwise $\hsame$, displayed
$\Cont$, $\Pkg$ provenance, and local $\NameCert_{\ZNormalUp}$ data.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:znormal-root-fuel-obligation-surface}. It identifies
the complete route inventory used by a root-facing terminal-normality read.

Apply \autoref{thm:znormal-normal-form-consumer-readiness}. Any downstream
consumer receives terminal normality through that same inventory, so an
excluded host-side object cannot be introduced by changing the consumer.

Finally use \autoref{thm:znormal-fuel-normality-nonescape},
\autoref{thm:znormal-root-unblock-nonescape-ledger}, and
\autoref{thm:znormal-terminal-host-classifier-route-nonescape}. These results
remove divergence, host conversion, quotient computation, unrestricted
evaluation, global normalization, and off-packet classifier routes from the
accepted surface. Hence the fuel route is a finite BEDC route and not a host
normalization principle.
\end{proof}
