\begin{theorem}[$\ZNormalUp$ total-host decision surface]
\label{thm:znormal-total-host-decision-surface}
Every accepted $\ZNormalUp$ packet exposes a total-host decision surface through the displayed finite rows
$$
T,F,V,K,R,H,C,P,N.
$$
Terminal normality is read through $V$ over the typed endpoint $T$ and bounded fuel replay $F$; the normal-word row $K$ cites the $\ZeckendorfNormalUp$ and $\ZCarryUp$ sibling surfaces; the terminal continuation row $R$ cites the $\ContinuationTraceNormalFormUp$ surface; and the route is transported by $\hsame$, replayed by $\Cont$, packaged by $\Pkg$, and named by $\NameCert_{\ZNormalUp}$. The accepted decision rows contain no host conversion procedure, divergence oracle, quotient computation, unrestricted evaluator, or global normalizer.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalTotalHostDecisionSurface}
\begin{proof}
Start with the carrier and obligation packet of \autoref{def:znormal-carrier} and \autoref{def:znormal-total-host-obligation-packet}. Together they display exactly $T,F,V,K,R,H,C,P,N$, so the decision surface has no coordinate outside the finite $\BHist$ packet.

Read the sibling anchors next. The typed endpoint route is the one supplied by \autoref{ch:concrete-instances-typedreductionnormalform-namecert}; the finite normal-word route is constrained by \autoref{ch:concrete-instances-zeckendorf-normal-namecert} and \autoref{ch:concrete-instances-zcarry-namecert}; and the terminal continuation route is the one supplied by \autoref{ch:concrete-instances-continuationtracenormalform-namecert}. These anchors feed rows of the packet rather than a host conversion row.

Finally apply \autoref{thm:znormal-terminal-host-obligation-totality}. It assembles terminal normality, bounded fuel replay, sibling normal-word evidence, terminal readback, transport, replay, provenance, and local naming as the whole consumer-facing surface. Hence the total-host decision row is precisely the displayed $\BHist$, $\Cont$, $\hsame$, $\Pkg$, and $\NameCert$ surface.
\end{proof}

\begin{theorem}[$\ZNormalUp$ terminal-normality refusal stability]
\label{thm:znormal-terminal-normality-refusal-stability}
Let $Z=(T,F,V,K,R,H,C,P,N)$ and $Z'=(T',F',V',K',R',H',C',P',N')$ be accepted $\ZNormalUp$ packets related by componentwise $\hsame$ transport of the displayed rows. If a consumer request for $Z$ is refused because it asks for a divergence oracle, a host-conversion procedure, or a global-normalization row instead of terminal normality, then the corresponding transported request for $Z'$ is refused for the same reason. The refusal remains attached to the $\BHist$, $\Cont$, $\Pkg$, and local $\NameCert$ surface and is not converted into a transported host-side object.
\end{theorem}
\begin{proof}
Project both accepted packets through \autoref{def:znormal-carrier}. Componentwise transport moves only the rows $T,F,V,K,R,H,C,P,N$ and their primed counterparts, so it has no target coordinate for a divergence oracle, host conversion procedure, or global normalizer.

Use \autoref{thm:znormal-total-host-readback-separation}. Refusal of the excluded objects is not a side condition outside the packet; it is the separation of the finite total-host readback surface from host conversion, quotient computation, unrestricted evaluation, divergence detection, substrate halting, and global normalization.

The sibling surfaces remain component inputs under transport. Typed reduction normal-form, Zeckendorf normal form, local carry, continuation trace, and the normal-form consistency seal of \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert} are consumed through the displayed $K$ and $R$ rows and through $H,C,P,N$. Thus transporting the accepted packet preserves the same refusal ledger and never creates a transported host-side object.
\end{proof}

\begin{theorem}[$\ZNormalUp$ root-unblock NameCert exhaustion]
\label{thm:znormal-root-unblock-namecert-exhaustion}
The local $\NameCert_{\ZNormalUp}$ surface needed for root unblock is exhausted by the displayed terminal-normality, bounded-fuel, replay, provenance, and naming rows of the accepted packet. Concretely, carrier admission reads the $\BHist$ packet $T,F,V,K,R,H,C,P,N$; classifier and terminal-normality reads use $T,F,V,K,R$; transport and replay use $H$ and $C$; provenance and local naming use $P$ and $N$. No additional NameCert clause remains for host conversion, divergence detection, global normalization, quotient computation, unrestricted evaluation, or substrate halting.
\end{theorem}
\begin{proof}
Read the root carrier through \autoref{def:znormal-carrier} and the total-host obligation packet through \autoref{def:znormal-total-host-obligation-packet}. These definitions list the full root-unblock surface and identify the terminal-normality, fuel, replay, provenance, and naming rows.

Apply \autoref{thm:znormal-total-host-decision-surface}. It places the sibling typed endpoint, Zeckendorf normal-word, carry, continuation-trace, and normal-form consistency seal of \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert} inside the same finite row family, with $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ as the only structural routes.

Finally use \autoref{thm:znormal-terminal-normality-refusal-stability}. Since the excluded host-side requests remain refused under componentwise transport, there is no residual NameCert obligation beyond the displayed carrier, classifier, transport, replay, provenance, and naming rows. The root-unblock certificate is therefore exhausted by the local packet.
\end{proof}

\begin{theorem}[$\ZNormalUp$ total-host decision route exhaustion]
\label{thm:znormal-total-host-decision-route-exhaustion}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the terminal-host decision route is exhausted by the finite $\BHist$ display and its $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\ZNormalUp}$ rows. The route reads carrier admission from $T,F,V,K,R,H,C,P,N$, terminal decision from $T,F,V,K,R$, transport from $H$, continuation replay from $C$, provenance from $P$, and local naming from $N$. It contains no host conversion, divergence oracle, quotient computation, unrestricted evaluator, substrate-halting row, or global normalizer.
\end{theorem}
\begin{proof}
Begin with \autoref{def:znormal-carrier} and \autoref{def:znormal-total-host-obligation-packet}. They present $T,F,V,K,R,H,C,P,N$ as the whole accepted carrier and obligation packet, so every terminal-host read starts inside a finite $\BHist$ display.

Apply \autoref{thm:znormal-total-host-decision-surface}. The theorem identifies the decision surface with the typed endpoint, bounded fuel, terminal-normality, sibling normal-word, continuation readback, transport, replay, provenance, and naming rows rather than with a host-side evaluator.

Finally use \autoref{thm:znormal-terminal-normality-refusal-stability} and \autoref{thm:znormal-root-unblock-namecert-exhaustion}. The refused host-side requests stay refused under $\hsame$ transport, and the local root-unblock certificate has no remaining clause outside $\BHist$, $\Cont$, $\Pkg$, and $\NameCert_{\ZNormalUp}$. Hence the total-host decision route is exhausted by the displayed finite packet.
\end{proof}

\begin{theorem}[$\ZNormalUp$ terminal-host classifier route nonescape]
\label{thm:znormal-terminal-host-classifier-route-nonescape}
Let $Z=(T,F,V,K,R,H,C,P,N)$ be an accepted $\ZNormalUp$ packet. Any terminal-host classifier route that reaches the root-unblock surface factors through the displayed $\BHist$ rows $T,F,V,K,R,H,C,P,N$, with classifier reads on $T,F,V,K,R$, componentwise $\hsame$ transport on $H$, $\Cont$ replay on $C$, $\Pkg$ provenance on $P$, and $\NameCert_{\ZNormalUp}$ naming on $N$. No classifier branch escapes to a host conversion procedure, divergence oracle, quotient computation, unrestricted evaluator, substrate-halting row, or global normalizer.
\end{theorem}
\begin{proof}
Project the route through \autoref{def:znormal-carrier} and \autoref{def:znormal-total-host-obligation-packet}. The only classifier-readable coordinates are the displayed terminal, fuel, terminal-normality, sibling normal-word, and continuation rows, with transport, replay, provenance, and naming carried by $H,C,P,N$.

Use \autoref{thm:znormal-total-host-decision-surface} to identify the classifier as a consumer of that finite decision surface. It receives no independent host conversion row and no quotient or halting computation row.

Now apply \autoref{thm:znormal-terminal-normality-refusal-stability}. A request that attempts to leave the displayed route is refused before transport can turn it into a host-side object.

\autoref{thm:znormal-root-unblock-namecert-exhaustion} then closes the route at the local $\NameCert_{\ZNormalUp}$ surface. Since root unblock has no residual naming obligation beyond the finite packet, the terminal-host classifier route has no escape branch.
\end{proof}

\begin{theorem}[$\ZNormalUp$ normal-form readiness support totality]
\label{thm:znormal-normal-form-readiness-support-totality}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
normal-form readiness for terminal-host use is supported exactly by the finite carrier, classifier, transport, replay, provenance, and naming rows of $Z$. The readiness support consists of the $\BHist$ rows $T,F,V,K,R,H,C,P,N$, the $\hsame$ row $H$, the $\Cont$ row $C$, the $\Pkg$ row $P$, and the local $\NameCert_{\ZNormalUp}$ row $N$. It has no host conversion, divergence oracle, quotient computation, unrestricted evaluator, substrate-halting row, or global normalizer.
\end{theorem}
\begin{proof}
Read the accepted packet through \autoref{def:znormal-carrier} and \autoref{def:znormal-total-host-obligation-packet}. Normal-form readiness is therefore anchored in the same finite $\BHist$ tuple $T,F,V,K,R,H,C,P,N$ as terminal-host decision.

\autoref{thm:znormal-total-host-decision-surface} supplies the readiness support from the terminal endpoint, bounded fuel, terminal normality, sibling normal-word evidence, continuation readback, transport, replay, provenance, and naming rows. These are BEDC rows of the packet, not a global normalizer or unrestricted evaluator.

Apply \autoref{thm:znormal-terminal-normality-refusal-stability} to rule out conversion of refused host-side requests into readiness data. Then apply \autoref{thm:znormal-root-unblock-namecert-exhaustion} to identify the local NameCert surface as complete for root unblock.

Thus every support row needed by terminal-host normal-form readiness is already one of the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\ZNormalUp}$ rows displayed by $Z$.
\end{proof}
