\begin{theorem}[$\ZNormalUp$ TasteGate scope binding]
\label{thm:znormal-tastegate-scope-binding}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the finite rows $T,F,V,K,R,H,C,P,N$ are the exact field surface later consumed
by \texttt{Nontrivial ZNormalUp} and \texttt{FieldFaithful ZNormalUp}. The
TasteGate-facing surface reads typed endpoint, finite fuel, terminal
normality, finite sibling normal-word evidence, terminal continuation,
componentwise transport, displayed continuation, package provenance, and local
NameCert rows, and it exports no host conversion, quotient computation,
unrestricted evaluation, divergence oracle, or global normalizer.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_tastegate\_scope\_binding}
\begin{proof}
Begin with finite-fuel carrier admission and the local NameCert obligations.
They expose exactly $T,F,V,K,R,H,C,P,N$ as one finite $\BHist$ packet and bind
the same rows to the local $\NameCert_{\ZNormalUp}$ surface.

Apply the displayed TasteGate contract row through the normal-form package. The
consumer receives the terminal and sibling evidence already routed through the
packet, so the later Nontrivial and FieldFaithful instances consume the same
field surface rather than a host-side computation.

Finally use the fuel non-escape and total-host refusal rows. Since the packet
contains no coordinate for host conversion, quotient computation, unrestricted
evaluation, divergence, or global normalization, the TasteGate scope is exactly
the displayed finite field surface.
\end{proof}

\begin{theorem}[$\ZNormalUp$ terminal fuel field scope]
\label{thm:znormal-terminal-fuel-field-scope}
Every terminal-normality read of an accepted $\ZNormalUp$ packet factors
through the finite chain
$$
T \to F \to V \to R,
$$
with $K$ available only as finite Zeckendorf and carry-facing sibling evidence.
The structural rows $H,C,P,N$ transport, replay, package, and name this chain;
they do not replace it by host conversion, quotient computation, unrestricted
evaluation, divergence detection, or global normalization.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_terminal\_fuel\_field\_scope}
\begin{proof}
Use \autoref{thm:znormal-terminal-normality-consumer-gate}. It places every
continuation read behind the typed endpoint $T$, finite fuel $F$, and
terminal-normality row $V$ in the same packet.

Next apply terminal readback exactness and sibling normal-word handoff. The
readback row is $R$, while $K$ remains finite sibling evidence through the
Zeckendorf and carry-facing surfaces.

The route transport theorem supplies the only structural movement. Rows
$H,C,P,N$ transport, replay, package, and name the finite chain, and fuel
non-escape rules out any replacement by an omitted host or global object.
\end{proof}

\begin{theorem}[$\ZNormalUp$ total-host consumer scope]
\label{thm:znormal-total-host-consumer-scope}
No total-host consumer of an accepted $\ZNormalUp$ packet can read divergence,
host conversion, quotient computation, unrestricted evaluation, or global
normalization from the packet. Every such consumer is confined to
$$
T,F,V,K,R,H,C,P,N
$$
and to the finite sibling routes named by $K$ and $R$.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_total\_host\_consumer\_scope}
\begin{proof}
Start with the total-host refusal exhaustion theorem. It already confines
total-host requests to the displayed packet and the finite sibling surfaces
cited by the normal-word and continuation rows.

Use the terminal fuel field scope above to isolate the terminal-normality
chain. Then use the continuation normal-word pullback to keep $K$ and $R$ in
one transported, replayed, packaged, and named packet.

Finally apply the no-divergence oracle ledger and root non-escape ledger.
Together they exhaust all consumer reads through the displayed rows, so none
of the excluded host, quotient, evaluator, divergence, or global-normalization
objects is available.
\end{proof}

\begin{theorem}[$\ZNormalUp$ terminal fuel row exhaustion]
\label{thm:znormal-terminal-fuel-row-exhaustion}
Every terminal-normality read of an accepted $\ZNormalUp$ packet is exhausted
by the rows
$$
T,F,V,R,H,C,P,N.
$$
The row $K$ contributes only the finite Zeckendorf and carry-facing sibling
normal-word surface already available to the packet, and the TasteGate-facing
consumer surface is the same field surface later used by
\texttt{Nontrivial ZNormalUp} and \texttt{FieldFaithful ZNormalUp}.
\end{theorem}
\begin{proof}
Apply \autoref{thm:znormal-terminal-fuel-field-scope}. It places each
terminal-normality read behind $T,F,V,R$ and uses $H,C,P,N$ only as transport,
replay, package, and naming rows.

Next use \autoref{thm:znormal-total-host-consumer-scope}. A consumer that asks
for host conversion, quotient computation, divergence, unrestricted
evaluation, or global normalization receives no additional row.

The remaining sibling evidence is exactly the finite handoff of
\autoref{thm:znormal-sibling-normalword-handoff}. Thus the TasteGate boundary
seen by later Nontrivial and FieldFaithful instances is the displayed finite
surface, not a host evaluator.
\end{proof}

\begin{theorem}[$\ZNormalUp$ normal-word sibling exactness]
\label{thm:znormal-normal-word-sibling-exactness}
The normal-word row $K$ of an accepted $\ZNormalUp$ packet is exact only
through the Zeckendorf and carry-facing sibling routes cited by
\autoref{thm:znormal-sibling-normalword-handoff}. Together with the
continuation readback row $R$, it is transported through $H,C,P,N$ and not
through host conversion, quotient computation, divergence, unrestricted
evaluation, or global normalization.
\end{theorem}
\begin{proof}
Start with \autoref{thm:znormal-sibling-normalword-handoff}. It identifies $K$
with the finite Zeckendorf and carry-facing sibling normal-word evidence.

Now apply \autoref{thm:znormal-continuation-normal-word-pullback}. This places
$K$ and $R$ on one transported route and permits only the structural rows
$H,C,P,N$ to move that route across the packet.

Finally use \autoref{thm:znormal-total-host-consumer-scope}. Since the packet
exports no host or quotient-facing normalizer, the exactness of $K$ is exactly
the sibling exactness already named in the finite rows.
\end{proof}

\begin{theorem}[$\ZNormalUp$ total-host refusal package]
\label{thm:znormal-total-host-refusal-package}
For every accepted $\ZNormalUp$ packet, the public refusal package excludes
host conversion, quotient computation, divergence oracle, unrestricted
evaluator, and global normalizer. All admitted reads factor through
$$
T,F,V,K,R,H,C,P,N,
$$
with terminal-normality routed by $T,F,V,R,H,C,P,N$ and sibling normal-word
evidence routed by $K$ through the Zeckendorf and carry-facing sibling surface.
\end{theorem}
\begin{proof}
First combine \autoref{thm:znormal-terminal-fuel-row-exhaustion} with
\autoref{thm:znormal-normal-word-sibling-exactness}. These rows separate the
terminal-normality route from the sibling normal-word route while keeping both
inside the same finite packet.

Next apply \autoref{thm:znormal-total-host-consumer-scope}. It refuses every
total-host request whose requested object has no coordinate in
$T,F,V,K,R,H,C,P,N$.

The TasteGate surface is therefore explicit: later Nontrivial and
FieldFaithful instances consume the same finite field surface, and no hidden
host conversion, quotient computation, divergence oracle, unrestricted
evaluator, or global normalizer is packaged.
\end{proof}

\begin{theorem}[$\ZNormalUp$ root TasteGate field surface]
\label{thm:znormal-root-tastegate-field-surface}
For every accepted $\ZNormalUp$ packet
$$
Z=(T,F,V,K,R,H,C,P,N),
$$
the TasteGate-facing field surface is exactly the displayed tuple $T,F,V,K,R,H,C,P,N$. The surface reads terminal normality and sibling normal-word evidence only through those rows; it cannot collapse into host conversion, quotient normalization, unrestricted evaluation, a divergence oracle, or a global normalizer.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZNormalTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier and local NameCert obligations. They expose $T,F,V,K,R,H,C,P,N$ as the complete field inventory and leave no additional coordinate for a host-side converter or quotient normalizer.

Use the TasteGate scope binding and total-host refusal package. The first binds the future Nontrivial and FieldFaithful read to the same tuple, while the second refuses every consumer request whose object is not carried by the tuple.

The field surface is therefore exact. Any attempted collapse to host conversion or quotient normalization would require a coordinate absent from the carrier, so the TasteGate-facing read remains the finite BEDC packet surface.
\end{proof}

\begin{theorem}[$\ZNormalUp$ terminal normality scope package]
\label{thm:znormal-terminal-normality-scope-package}
Every terminal-normality read of an accepted $\ZNormalUp$ packet factors through
$$
T,F,V,R,H,C,P,N,
$$
with $K$ available only as finite sibling evidence through the Zeckendorf and carry-facing normal-word surface. No terminal-normality consumer can replace this route by host conversion, quotient normalization, unrestricted evaluation, divergence detection, or global normalization.
\end{theorem}
\begin{proof}
Begin with terminal fuel row exhaustion. It places each terminal-normality read behind $T,F,V,R$ and makes $H,C,P,N$ the only transport, replay, package, and naming rows.

Next read the sibling evidence. Normal-word sibling exactness keeps $K$ on the finite Zeckendorf and carry-facing route, so $K$ supports the terminal read only as sibling evidence and not as a host evaluator.

Finally apply the root TasteGate field surface. The terminal-normality consumer receives the same finite tuple surface, and the excluded host or quotient objects have no field from which they could be read.
\end{proof}

\begin{theorem}[$\ZNormalUp$ normal-word continuation scope lock]
\label{thm:znormal-normal-word-continuation-scope-lock}
Before any downstream normal-form consumer reads an accepted $\ZNormalUp$ packet, the normal-word row $K$ and continuation row $R$ are jointly scoped through $\ZeckendorfNormalUp$, $\ZCarryUp$, and $\ContinuationTraceNormalFormUp$. The joint scope is transported, replayed, packaged, and named only through $H,C,P,N$ and cannot be reopened as host conversion, quotient normalization, unrestricted evaluation, divergence detection, or global normalization.
\end{theorem}
\leanchecked{BEDC.Derived.ZnormalUp.ZnormalPacket\_normal\_word\_continuation\_scope\_lock}
\begin{proof}
Start with normal-word sibling exactness. It binds $K$ to the finite Zeckendorf and carry-facing sibling routes, so any normal-word read is already scoped before downstream consumption.

Now apply the continuation normal-word pullback. It places $K$ and $R$ on one finite route through $H,C,P,N$, with $R$ supplied by the continuation terminal surface and not by a detached evaluator.

Use the terminal normality scope package to close the downstream read. Since the consumer sees only the joined $K,R$ route inside the displayed packet, no host conversion, quotient normalization, unrestricted evaluation, divergence detector, or global normalizer can reopen the scope.
\end{proof}
