\section{The certificate}
\label{sec:measure-certificate}

\begin{theorem}[Measure carrier and classifier stability]
\label{thm:measure-carrier-and-classifier-stability}
Let $M$ and $N$ be $\MeasureUp$ carriers as in \autoref{def:measure-carrier-specification}, related by the classifier of \autoref{def:measure-classifier-specification}. If $E$ is a displayed event of $M$, $E'$ is a displayed event of $N$, and the event presentations satisfy $\hsame(E,E')$, then the measurable witness for $E$ in $\mathcal A_M$ transports to a measurable witness for $E'$ in $\mathcal A_N$. Moreover the visible measure endpoints satisfy
$$
\mu_M(E)\sim_R\mu_N(E')
$$
through $\mathsf{RealConstantHistoryClassifier}$ and the $\RealUp$ classifier of \autoref{def:real-classifier-specification}.
\end{theorem}
\begin{proof}
The shared event-carrier component of \autoref{def:measure-classifier-specification} is exactly the transport rule for displayed event witnesses. Apply it to the $\hsame(E,E')$ comparison to move the event witness and its measurable row from $M$ to $N$.

The endpoint component of the classifier reads the two ledger endpoints attached to the transported measurable event. Since the carrier specification records the event witness, measurable witness, and $\RealUp$ endpoint in the same visible ledger, the endpoint comparison is the displayed $\mathsf{RealConstantHistoryClassifier}$ row.

Finally, \autoref{def:real-classifier-specification} identifies that row as a valid $\RealUp$ classifier comparison. No quotient of event codes and no host equality of subsets is introduced.
\end{proof}

\begin{theorem}[MeasureUp classifier stability obligations]
\label{thm:measureup-classifier-stability-obligations}
For a $\MeasureUp$ carrier with inventory
\autoref{def:measureup-carrier-obligation-inventory}, componentwise $\hsame$
of carrier packages transports every row named by the inventory. In particular,
if two packages are componentwise $\hsame$, then measurable membership in
$\mathcal{A}$, the $\RealUp$-valued measure rows for $\mu$, the
$\sigma$-algebra closure rows, and the $\RealUp$ classifier on $\mu$-values are
preserved across the transport.
\end{theorem}
\begin{proof}
Unpack the carrier inventory. The event carrier, the measurable predicate, the
measure map, and the empty, binary-union, countable-union, and
complement/relative-difference rows are separate components of the same
$\mathsf{BHist}$ package.

Componentwise $\hsame$ supplies a transport witness for each component. Applying
the measurable-set component transports membership in $\mathcal{A}$, and
applying the closure-row components transports the empty, binary-union, and
countable-union witnesses. The same componentwise projection transports the
relative-difference event, its inclusion readback, its disjointness witness,
and its binary-union readback.

It remains to identify the value rows. The $\mu$-congruence component sends
transported measurable events to transported $\RealUp$ values, and the
$\RealUp$ classifier of \autoref{def:real-classifier-specification} composes
those comparisons inside the codomain. Hence the classifier on $\mu$-values is
stable under the same componentwise carrier transport.
\end{proof}

\begin{theorem}[MeasureUp sigma-additive certificate obligations]
\label{thm:measureup-sigma-additive-certificate-obligations}
For a $\MeasureUp$ carrier with inventory
\autoref{def:measureup-carrier-obligation-inventory}, a $\MeasureUp$
certificate consists of the following rows:
\begin{enumerate}
  \item empty-event membership $\varnothing\in\mathcal{A}$;
  \item binary disjoint-union closure in $\mathcal{A}$;
  \item countable disjoint-union closure in $\mathcal{A}$ for
  StreamName-style measurable families;
  \item complement/relative-difference closure for displayed inclusions
  $B\subseteq A$ of measurable events in the same carried fiber;
  \item $\sigma$-additivity into the $\RealUp$ countable-sum classifier;
  \item classifier-stable head-tail readback for those countable sums.
\end{enumerate}
With these rows, \autoref{thm:measure-empty-set-zero-from-sigma-additivity} and
\autoref{thm:measure-finite-disjoint-union-additivity} are consequences of the
certificate package, and the displayed relative-difference row supplies the
finite difference readback of
\autoref{thm:measure-relative-difference-additivity}.
\end{theorem}
\begin{proof}
The first row gives the all-empty measurable sequence used for the zero law.
The countable disjoint-union row identifies its union as the empty event, and
the $\sigma$-additivity row compares $\mu(\varnothing)$ with the associated
$\RealUp$ countable sum.

Head-tail readback splits that sum into its head and tail. The classifier
stability theorem transports the tail back to the original all-empty sum, and
the additive $\AbGroupUp$ row then cancels the repeated summand exactly as in
\autoref{thm:measure-empty-set-zero-from-sigma-additivity}.

For the finite disjoint-union law, use the measurable sequence whose first two
terms are the given disjoint events and whose remaining terms are empty. Binary
closure supplies measurability of $A\cup B$, countable closure supplies the same
event as the countable union, and $\sigma$-additivity compares its measure with
the corresponding countable sum.

Two applications of head-tail readback expose the first two summands. The empty
tail is classified as $0_R$ by the zero law, and the additive $\AbGroupUp$ row
removes that unit. The resulting comparison is the statement of
\autoref{thm:measure-finite-disjoint-union-additivity}.

For displayed inclusions $B\subseteq A$, the complement/relative-difference row
supplies the measurable event $A\setminus B$, the disjointness of $B$ and
$A\setminus B$, and the binary-union readback to $A$. Feeding those rows into
finite disjoint-union additivity gives the finite difference comparison.
\end{proof}

\begin{theorem}[Measure finite-support countable readback]
\label{thm:measure-finite-support-countable-readback}
Let $M$ be a $\MeasureUp$ carrier as in \autoref{def:measure-carrier-specification}. Let $E_\bullet$ be a pairwise-disjoint measurable sequence such that $E_n=\varnothing$ for every $n\geq2$. Write
$$
S:=\Sigma_\mu(E_\bullet),\qquad
T:=\Sigma_\mu(E_{\bullet+1}),\qquad
U:=\Sigma_\mu(E_{\bullet+2}).
$$
If the carrier supplies classifier-stable head-tail readback, pointwise countable-sum stability, and the additive $\AbGroupUp$ row of \autoref{def:abgroup-carrier} with zero $0_R$, then
$$
S\sim_R\mu(E_0)+\mu(E_1).
$$
\end{theorem}
\begin{proof}
Apply the head-tail row to the original sequence. It gives $S\sim_R\mu(E_0)+T$. Apply the same row to the shifted sequence. It gives $T\sim_R\mu(E_1)+U$.

It remains to read back the empty tail. Let $F_n:=\varnothing$ for all $n$. Since $E_{n+2}=\varnothing$ by hypothesis, pointwise countable-sum stability gives $U\sim_R\Sigma_\mu(F_\bullet)$. The constant-empty $\sigma$-additivity row identifies $\mu(\varnothing)$ with $\Sigma_\mu(F_\bullet)$, and \autoref{thm:measure-empty-set-zero-from-sigma-additivity} identifies $\mu(\varnothing)$ with $0_R$.

Transport this comparison through the additive congruence supplied by \autoref{def:abgroup-carrier}. The right-unit law then reads $\mu(E_1)+U$ as $\mu(E_1)$, and a final congruence step reads $\mu(E_0)+T$ as $\mu(E_0)+\mu(E_1)$.
\end{proof}

\begin{theorem}[Measure certificate obligation threshold]
\label{thm:measure-certificate-obligation-threshold}
A $\MeasureUp$ NameCert obligation threshold is reached by the following paper-side data: a carrier satisfying \autoref{def:measure-carrier-specification}, a classifier satisfying \autoref{def:measure-classifier-specification}, the stability row of \autoref{thm:measure-carrier-and-classifier-stability}, the finite-support countable readback row of \autoref{thm:measure-finite-support-countable-readback}, the empty-set-zero theorem \autoref{thm:measure-empty-set-zero-from-sigma-additivity}, and the finite disjoint-union additivity theorem \autoref{thm:measure-finite-disjoint-union-additivity}. These data provide the carrier transport, classifier transport, $\sigma$-additive readback, zero endpoint, binary additivity, and visible ledger rows required by the public $\MeasureUp$ certificate surface.
\end{theorem}
\begin{proof}
The carrier and classifier definitions supply the public surface: event witnesses, measurable witnesses, endpoint rows, and classifier movement are all visible BHist and $\RealUp$ rows. The stability theorem is the transport field of the surface, with endpoint movement discharged by \autoref{def:real-classifier-specification}.

The finite-support theorem turns the countable-sum row into the binary readback needed by finite disjoint union. The empty-set-zero theorem supplies the additive zero endpoint, and the additive $\AbGroupUp$ row of \autoref{def:abgroup-carrier} supplies the congruence and unit laws used in that readback.

Finally, \autoref{thm:measure-finite-disjoint-union-additivity} packages these rows into the displayed binary additivity clause. The cancellation step used by the zero endpoint is exactly the group row cited in \autoref{thm:group-left-absorb-right-factor-unit}, so the threshold is assembled from visible certificate fields rather than from external set equality.
\end{proof}

\begin{theorem}[Measure empty set is zero]
\label{thm:measure-empty-set-zero-from-sigma-additivity}
For a $\MeasureUp$ carrier as in \autoref{sec:measure-carrier}, let $\mathcal{A}$ be its designated $\sigma$-algebra, let $\mu$ be its $\RealUp$-valued measure map, and write $x\sim_R y$ for the $\RealUp$ classifier of \autoref{def:real-classifier-specification}. Suppose $\varnothing\in\mathcal{A}$, and suppose the $\MeasureUp$ certificate supplies $\sigma$-additivity for every pairwise-disjoint measurable sequence, together with classifier-stable head-tail readback for the resulting countable $\RealUp$ sum. If the target $\RealUp$ addition is carried by its additive $\AbGroupUp$ row with zero $0_R$, then
$$
\mu(\varnothing)\sim_R 0_R.
$$
\end{theorem}
\begin{proof}
Let $E_n:=\varnothing$ for every $n:\mathbb{N}$. The hypothesis $\varnothing\in\mathcal{A}$ makes every $E_n$ measurable. The sequence is pairwise disjoint, and its union is again $\varnothing$.

Let $S$ be the countable $\RealUp$ sum $\sum_{n=0}^{\infty}\mu(E_n)$. The $\sigma$-additivity row gives
$$
\mu(\varnothing)\sim_R S.
$$
The head-tail row for this sum gives
$$
S\sim_R\mu(E_0)+\sum_{n=1}^{\infty}\mu(E_n).
$$
Since $E_0=\varnothing$, the first summand is $\mu(\varnothing)$. The tail sequence $(E_{n+1})_{n\geq0}$ is pointwise the same empty sequence as $(E_n)_{n\geq0}$, so countable-sum classifier stability gives
$$
\sum_{n=1}^{\infty}\mu(E_n)\sim_R S.
$$
Composing this with the $\sigma$-additivity comparison and transporting the right summand through addition yields
$$
S\sim_R\mu(\varnothing)+\mu(\varnothing).
$$
Composing once more with $\mu(\varnothing)\sim_R S$ gives
$$
\mu(\varnothing)\sim_R\mu(\varnothing)+\mu(\varnothing).
$$
By symmetry, $\mu(\varnothing)+\mu(\varnothing)\sim_R\mu(\varnothing)$.

The additive $\AbGroupUp$ row described in \autoref{def:abgroup-carrier} gives the group hypotheses for $+$ and $0_R$. Applying \autoref{thm:group-left-absorb-right-factor-unit} with $a=\mu(\varnothing)$ and $b=\mu(\varnothing)$ forces the right summand to the additive unit, yielding $\mu(\varnothing)\sim_R0_R$.
\end{proof}

\begin{theorem}[Measure finite disjoint-union additivity]
\label{thm:measure-finite-disjoint-union-additivity}
For a $\MeasureUp$ carrier as in \autoref{sec:measure-carrier}, let $\mathcal{A}$ be its designated $\sigma$-algebra, let $\mu$ be its $\RealUp$-valued measure map, and write $x\sim_R y$ for the $\RealUp$ classifier of \autoref{def:real-classifier-specification}. Let $A,B\in\mathcal{A}$ be disjoint, and let $A\cup B$ be the measurable binary union supplied by the $\sigma$-algebra row. Suppose $\varnothing\in\mathcal{A}$, and suppose the $\MeasureUp$ certificate supplies $\sigma$-additivity for every pairwise-disjoint measurable sequence, together with classifier-stable head-tail readback and pointwise classifier stability for the resulting countable $\RealUp$ sums. If the target $\RealUp$ addition is carried by its additive $\AbGroupUp$ row with zero $0_R$, then
$$
\mu(A\cup B)\sim_R\mu(A)+\mu(B).
$$
\end{theorem}
\begin{proof}
Define a measurable sequence by $E_0:=A$, $E_1:=B$, and $E_n:=\varnothing$ for every $n\geq2$. Each term is measurable because $A,B,\varnothing\in\mathcal{A}$. The sequence is pairwise disjoint: the only nonempty pair to check is $A$ against $B$, and this is the displayed disjointness hypothesis. Its countable union is exactly $A\cup B$.

Let
$$
S:=\sum_{n=0}^{\infty}\mu(E_n),\qquad
T:=\sum_{n=0}^{\infty}\mu(E_{n+1}),\qquad
U:=\sum_{n=0}^{\infty}\mu(E_{n+2}).
$$
The $\sigma$-additivity row gives
$$
\mu(A\cup B)\sim_R S.
$$
The first head-tail readback gives
$$
S\sim_R\mu(E_0)+T,
$$
hence $S\sim_R\mu(A)+T$. The second head-tail readback gives
$$
T\sim_R\mu(E_1)+U,
$$
hence $T\sim_R\mu(B)+U$.

It remains to identify the empty tail. Let $F_n:=\varnothing$ for every $n$, and let $S_{\varnothing}:=\sum_{n=0}^{\infty}\mu(F_n)$. Since $E_{n+2}=F_n$ for every $n$, pointwise classifier stability of the countable sum gives
$$
U\sim_R S_{\varnothing}.
$$
Applying $\sigma$-additivity to the all-empty sequence gives $\mu(\varnothing)\sim_R S_{\varnothing}$, while \autoref{thm:measure-empty-set-zero-from-sigma-additivity} gives $\mu(\varnothing)\sim_R0_R$. By symmetry and transitivity of the $\RealUp$ classifier, $S_{\varnothing}\sim_R0_R$, and therefore
$$
U\sim_R0_R.
$$

The additive $\AbGroupUp$ row of \autoref{def:abgroup-carrier} supplies addition congruence and the right-unit law. Transporting $U\sim_R0_R$ through addition gives
$$
\mu(B)+U\sim_R\mu(B)+0_R\sim_R\mu(B),
$$
so $T\sim_R\mu(B)$. Transporting this comparison through addition with the fixed left summand $\mu(A)$ gives
$$
\mu(A)+T\sim_R\mu(A)+\mu(B).
$$
Composing this with $S\sim_R\mu(A)+T$ and with $\mu(A\cup B)\sim_R S$ yields the displayed classification.
\end{proof}

\begin{theorem}[Measure complement row transport]
\label{thm:measure-complement-row-transport}
Let $M$ and $N$ be $\MeasureUp$ carriers as in
\autoref{def:measure-carrier-specification}, and suppose
$M\sim_{\MeasureUp}N$ through the public classifier of
\autoref{def:measure-classifier-specification}. If $A$ and $B$ are displayed
measurable events of $M$ with displayed inclusion $B\subseteq A$, then the
complement/relative-difference row of
\autoref{def:measure-complement-difference-row} transports the event
$A\setminus B$, its measurable witness, its disjointness witness against $B$,
its binary-union readback $B\cup(A\setminus B)\sim_M A$, and its $\RealUp$
measure endpoint to the corresponding row of $N$.
\end{theorem}
\begin{proof}
Project the public classifier into its componentwise $\hsame$ fields. These
fields transport the carried fiber, the two event presentations, their
measurable witnesses, and the displayed inclusion witness from $M$ to $N$.

Apply the stability clause in
\autoref{def:measure-complement-difference-row} to those transported inputs.
It returns the target relative-difference event together with the measurable,
disjointness, and binary-union readback fields.

The remaining endpoint comparison is the value component of the same row. Read
that component through $\mathsf{RealConstantHistoryClassifier}$ and then
through the $\RealUp$ classifier supplied by
\autoref{def:real-classifier-specification}.
\end{proof}

\begin{theorem}[Measure relative-difference disjoint decomposition]
\label{thm:measure-relative-difference-disjoint-decomposition}
Let $M$ be a $\MeasureUp$ carrier as in \autoref{sec:measure-carrier}. Let
$A$ and $B$ be displayed measurable events in the same carried fiber, and
suppose the public event readback displays $B\subseteq A$. Then the
complement/relative-difference row supplies a measurable event
$A\setminus B$ such that $B$ and $A\setminus B$ are disjoint and the binary
union $B\cup(A\setminus B)$ is classified as $A$ in the public $\MeasureUp$
event classifier.
\end{theorem}
\begin{proof}
Read the complement/relative-difference row of
\autoref{def:measure-complement-difference-row} at the carried fiber of $M$.
The hypotheses give exactly the row inputs: two measurable events and a
displayed inclusion $B\subseteq A$ in that fiber.

Project the row. Its first projection is the measurable event
$A\setminus B$. The next projections are the disjointness witness for $B$ and
$A\setminus B$ and the binary-union readback classifying
$B\cup(A\setminus B)$ as $A$.

These projections are already ledger rows of the public carrier surface, so no
host-level set subtraction or quotient equality is introduced.
\end{proof}

\begin{theorem}[Measure relative-difference additivity]
\label{thm:measure-relative-difference-additivity}
For a $\MeasureUp$ carrier as in \autoref{sec:measure-carrier}, let
$\mathcal{A}$ be its designated $\sigma$-algebra, let $\mu$ be its
$\RealUp$-valued measure map, and write $x\sim_R y$ for the $\RealUp$
classifier of \autoref{def:real-classifier-specification}. Let
$A,B\in\mathcal{A}$ be displayed events in the same carried fiber, and suppose
the public event readback displays $B\subseteq A$. If the certificate supplies
the complement/relative-difference row of
\autoref{def:measure-complement-difference-row} and the hypotheses of
\autoref{thm:measure-finite-disjoint-union-additivity} for the pair
$B,A\setminus B$, then
$$
\mu(A)\sim_R\mu(B)+\mu(A\setminus B).
$$
\end{theorem}
\begin{proof}
Apply
\autoref{thm:measure-relative-difference-disjoint-decomposition} to the
displayed inclusion $B\subseteq A$. This gives measurability of
$A\setminus B$, disjointness of $B$ and $A\setminus B$, and the binary-union
readback classifying $B\cup(A\setminus B)$ as $A$.

Apply \autoref{thm:measure-finite-disjoint-union-additivity} to the disjoint
pair $B$ and $A\setminus B$. The theorem gives
$$
\mu(B\cup(A\setminus B))\sim_R\mu(B)+\mu(A\setminus B).
$$

Use the binary-union readback from the relative-difference row to transport the
left endpoint from $\mu(B\cup(A\setminus B))$ to $\mu(A)$ through the
$\MeasureUp$ event classifier and then through the $\RealUp$ value classifier.
Composing that endpoint transport with the finite disjoint-union comparison
gives the displayed finite difference law.
\end{proof}

\begin{theorem}[MeasureUp NameCert obligation package]
\label{thm:measure-namecert-obligation-package}
The rows displayed in
\autoref{def:measure-sigma-algebra-carrier-surface}, together with the
classifier transport of
\autoref{thm:measure-carrier-classifier-obligation}, the complement transport
of \autoref{thm:measure-complement-row-transport}, the sigma-additivity
classification of \autoref{thm:measure-sigma-additivity-obligation}, the
ledger exactness of \autoref{thm:measure-ledger-exactness-obligation}, and the
three consequence theorems
\autoref{thm:measure-empty-set-zero-from-sigma-additivity} and
\autoref{thm:measure-finite-disjoint-union-additivity} and
\autoref{thm:measure-relative-difference-additivity}, form the
$\MeasureUp$ NameCert obligation package. This package is the measure substrate
consumed by $\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$.
\end{theorem}
\begin{proof}
Start with the carrier surface and project its visible event, value, stability,
and ledger rows. Repack those projections as the carrier and classifier side of
the $\MeasureUp$ certificate.

The carrier-classifier obligation supplies componentwise transport for every
displayed row, including the complement/relative-difference row. The
complement-row transport theorem makes that projection available under the
public classifier. The sigma-additivity obligation supplies the countable-union
classification needed by the measure consequences, while the ledger exactness
obligation identifies all hidden witnesses with their visible rows.

Finally include the empty-zero, finite disjoint-union, and
relative-difference consequence theorems as the core theorem rows of the
package. The downstream chapters named in the statement consume only this
package surface: $\IntegralUp$ uses the measurable event, relative-difference,
and countable-sum rows, $\ProbSpaceUp$ uses the empty and disjoint-union rows,
and $\FunctionalAnalysisUp$ uses the $\RealUp$ value classifier and additive
compatibility rows.
\end{proof}

\begin{definition}[Measure event row coverage]
\label{def:measure-event-row-coverage}
For the $\MeasureUp$ sigma-algebra carrier surface of
\autoref{def:measure-sigma-algebra-carrier-surface}, the event row coverage
predicate is the assertion that every row consumed by a downstream certificate
is attached to a visible $\mathsf{BHist}$ ledger row of that carrier surface.
Concretely, the covered rows are:
\begin{enumerate}
  \item every measurable event read by the measurable-family predicate
  $\mathcal{A}$;
  \item the empty-event row;
  \item every binary-union row, including its disjointness witness when the
  union is read as a disjoint union;
  \item every countable-union row for a StreamName-style measurable family,
  together with its pairwise-disjointness witness when sigma-additivity is
  invoked;
  \item every $\RealUp$ endpoint row $\mu(E)$ classified by the measure-value
  classifier;
  \item every countable-sum endpoint $\Sigma_\mu(E_\bullet)$ and every
  head-tail readback row attached to that endpoint.
\end{enumerate}
Coverage requires the attachment to be exact: the downstream consumer reads the
displayed $\mathsf{BHist}$ row, its $\hsame$ transport row, and the associated
$\RealUp$ endpoint classifier row, and it reads no additional event carrier,
choice object, quotient object, or analytic completion object from the
$\MeasureUp$ package.
\end{definition}

\begin{theorem}[Measure measurable family exactness]
\label{thm:measure-measurable-family-exactness}
For the $\MeasureUp$ sigma-algebra carrier surface, the event row coverage
predicate of \autoref{def:measure-event-row-coverage} gives coverage,
soundness, and completeness for the measurable-family classifier. Coverage
means that every measurable event, closure event, disjointness witness,
$\RealUp$ endpoint, and countable-sum endpoint used by the classifier is read
from a displayed ledger row. Soundness means that transporting a covered row
along the classifier gives the corresponding covered row in the target
presentation. Completeness means that every row available to the
measurable-family classifier is one of the rows listed in the coverage
predicate.
\end{theorem}
\begin{proof}
Unpack \autoref{def:measure-sigma-algebra-carrier-surface}. Its carrier,
stability, ledger, and exactness fields list exactly the measurable-event,
empty-event, binary-union, countable-union, disjointness, endpoint, and
countable-sum rows named in \autoref{def:measure-event-row-coverage}.

Coverage is therefore projection from the displayed carrier and ledger fields.
Each consumed event or endpoint row is attached to one of those fields by the
exactness clause of the surface.

Soundness is the transport statement of
\autoref{thm:measure-carrier-classifier-obligation}. Componentwise $\hsame$
moves the event rows, and the $\RealUp$ classifier moves the endpoint rows.
The ledger witness attached to a visible row is repacked after that visible row
has been transported.

Completeness is the exhaustion statement of
\autoref{thm:measure-ledger-exactness-obligation}. Since the ledger contains
only the listed rows and every hidden measurable-set or countable-sum witness
is attached to one of them, the measurable-family classifier has no further
row to read.
\end{proof}

\begin{theorem}[Measure probability normalization row]
\label{thm:measure-probability-normalization-row}
Let a covered $\MeasureUp$ package carry a total event row $\Omega$ whose
endpoint is classified as the probability unit:
$$
\mu(\Omega)\sim_R 1_R.
$$
Together with the empty-zero theorem
\autoref{thm:measure-empty-set-zero-from-sigma-additivity} and the finite
disjoint-union theorem
\autoref{thm:measure-finite-disjoint-union-additivity}, this row supplies the
normalization and finite-additivity rows consumed by $\ProbSpaceUp$. The claim
is only the projection of the total-event endpoint and the repacking of the
two named $\MeasureUp$ consequence theorems into the probability-space
certificate surface.
\end{theorem}
\begin{proof}
Project the total-event ledger row from the covered measure package. Its
endpoint comparison is already the normalization row required by
$\ProbSpaceUp$, namely $\mu(\Omega)\sim_R1_R$.

Next project the empty event, binary disjoint-union, endpoint, and additive
$\AbGroupUp$ rows exposed by \autoref{def:measure-event-row-coverage}. With
those rows in hand, \autoref{thm:measure-empty-set-zero-from-sigma-additivity}
gives the zero endpoint for the empty event.

Finally apply \autoref{thm:measure-finite-disjoint-union-additivity} to a
covered disjoint measurable pair. The result is exactly the finite-additivity
comparison used by the probability-space carrier; no sigma-additivity theorem
beyond the named $\MeasureUp$ package rows is imported into $\ProbSpaceUp$.
\end{proof}

\begin{theorem}[Measure integral premeasure consumption]
\label{thm:measure-integral-premeasure-consumption}
The $\IntegralUp$ premeasure interface may consume exactly the following rows
from the $\MeasureUp$ package: covered measurable-event rows, $\RealUp$
endpoint classifier rows, countable-sum endpoint rows, classifier-stable
head-tail readback rows, and the finite disjoint-union theorem
\autoref{thm:measure-finite-disjoint-union-additivity}. The same exposed
endpoint classifier and additive compatibility rows are the MeasureUp rows
available to $\FunctionalAnalysisUp$. These rows are precisely the public
surface supplied by \autoref{def:measure-certificate-surface},
\autoref{thm:measureup-sigma-additive-certificate-obligations}, and
\autoref{thm:measure-namecert-obligation-package}.
\end{theorem}
\begin{proof}
Begin with the public certificate surface of
\autoref{def:measure-certificate-surface}. Its projections provide the
measurable-family predicate, endpoint map, countable-sum endpoint, head-tail
readback row, and countable-sum classifier row.

The certificate obligation theorem
\autoref{thm:measureup-sigma-additive-certificate-obligations} identifies the
sigma-algebra rows and the sigma-additivity rows that make those projections
available to premeasure constructions. In particular it names the empty,
binary disjoint-union, countable disjoint-union, sigma-additivity, and
head-tail rows as the complete certificate rows used by the measure
consequences.

The NameCert package theorem
\autoref{thm:measure-namecert-obligation-package} repacks those rows as the
surface consumed by downstream analysis chapters. Reading that package through
\autoref{def:measure-event-row-coverage} leaves exactly the measurable-event,
endpoint, countable-sum, head-tail, and finite disjoint-union rows named in
the statement, with no additional carrier row available for $\IntegralUp$ or
$\FunctionalAnalysisUp$.
\end{proof}
