\begin{theorem}[Measure probability sigma dependency forward link]
\label{thm:measure-probability-sigma-dependency-forward-link}
Every $\ProbSpaceUp$ or $\IntegralUp$ consumer of an accepted $\MeasureUp$ packet must pass through the displayed sigma-event source rows, finite additivity and readback rows, and $\NameCert_{\MeasureUp}$ provenance before reading probability mass or integral value rows. The probability-facing route of \autoref{ch:concrete-instances-probspace-namecert} and the integral-facing route of \autoref{ch:concrete-instances-integral-namecert} therefore share the same $\MeasureUp$ dependency lattice rather than reading detached probability primitives, host measures, or independent value selectors.
\end{theorem}
\begin{proof}
Start with the sigma-event and source rows already displayed by the $\MeasureUp$ carrier. They name the measurable-event family, event classifier, empty-event boundary, and source value route before any probability or integration consumer appears.

Next read finite additivity and readback. These rows expose the disjoint-union mass ledger and the value route used by probability normalization and integral accumulation, so neither consumer can bypass the measure packet when it reads mass or integral data.

Finally pass through provenance and local naming. The $\Pkg$ and $\NameCert_{\MeasureUp}$ rows seal the shared dependency lattice, and the sibling probability and integral chapters can consume only the sealed event-and-value surface. No detached host measure, independent probability primitive, or selected value representative is exported.
\end{proof}
