\section{Measure root finite disjoint event envelope}
\label{sec:measure-root-finite-disjoint-event-envelope}

The finite disjoint event envelope is the kernel-facing $\MeasureUp$ package
used when downstream analysis chapters need a single finite event family,
its displayed union, its $\RealUp$ value fold, and the ledger rows that make
the finite support visible. It is a finite $\mathsf{BHist}$ event package,
not a sigma-complete event space or a standard bridge.

\begin{definition}[Measure root finite disjoint event envelope]
\label{def:measure-root-finite-disjoint-envelope}
The $\MeasureUp$ root finite disjoint event envelope is the ten-field package
attached to a displayed finite family $E_0,\ldots,E_{n-1}$ of
$\mathsf{BHist}$ event rows:
\begin{enumerate}
  \item source: the root public $\MeasureUp$ basis of
  \autoref{def:measure-root-public-obligation-basis}, the root event boundary
  of \autoref{sec:measure-root-event-boundary-package}, and the finite-support
  consumer front of \autoref{def:measure-root-finite-support-consumer-front};
  \item carrier: each $E_i$ is a carried $\mathsf{BHist}$ event row covered by
  the root $\MeasureUp$ event carrier;
  \item classifier: event comparison is the public $\MeasureUp$ classifier
  projected to componentwise $\hsame$ on displayed event histories and to the
  $\RealUp$ classifier on endpoint rows;
  \item disjointness: the family is pairwise disjoint after any classifier
  transport admitted by the root event boundary;
  \item finite union: the package displays a finite union row
  $U_n=E_0\sqcup\cdots\sqcup E_{n-1}$ in the same $\mathsf{BHist}$ ledger;
  \item value rows: each component has a $\RealUp$ value endpoint $\mu(E_i)$
  and the union has a $\RealUp$ value endpoint $\mu(U_n)$;
  \item fold row: the finite endpoint
  $\mathsf{fold}_R(\mu(E_0),\ldots,\mu(E_{n-1}))$ is built by the additive
  $\AbGroupUp$ row carried by $\RealUp$;
  \item support ledger: the finite family is embedded as a countable family
  with a constant empty tail, together with the visible finite-support
  ledger row;
  \item consumer boundary: $\IntegralUp$, $\ProbSpaceUp$, and
  $\FunctionalAnalysisUp$ may read only the carrier, finite union, value fold,
  and support-ledger rows named here;
  \item excluded surface: no sigma-completeness row, open-cover compactness
  row, quotient event equality, host set equality, analytic completion
  object, or $\StdBridge$ row is part of the envelope.
\end{enumerate}
\end{definition}

\begin{theorem}[Measure root finite disjoint carrier classifier]
\label{thm:measure-root-finite-disjoint-carrier-classifier}
The envelope of \autoref{def:measure-root-finite-disjoint-envelope} projects
carried $\MeasureUp$ event rows, classifier-stable pairwise disjointness, and
$\RealUp$ carrier rows from the existing root carrier, classifier, and event
boundary packages. Thus every component event, its transported disjointness
relation, its endpoint value, and the displayed finite union remain rows of
the same root $\mathsf{BHist}$ ledger.
\end{theorem}
\begin{proof}
Start with the carrier and classifier fields of
\autoref{def:measure-root-public-obligation-basis}. By
\autoref{thm:measure-root-public-obligation-basis-carrier}, each displayed
event row in the finite family is a carried $\mathsf{BHist}$ row, and
classifier transport keeps the attached endpoint and ledger witnesses on the
transported row.

Next read the same finite family through
\autoref{thm:measure-root-event-boundary-carrier}. The event boundary exposes
the visible event rows, finite union rows, endpoint rows, and ledger rows
without replacing the displayed event carrier by a host-level event object.

For disjointness, use
\autoref{thm:measure-root-event-boundary-classifier}. Its classifier is
componentwise $\hsame$ on displayed histories together with $\RealUp$
endpoint comparison. Pairwise disjointness in the envelope is therefore
stable exactly under the same classifier motion.

Finally project the endpoint rows through
\autoref{thm:measure-root-finite-support-carrier-readback}. The finite
support spine and the empty tail are read from the root carrier ledger, so
the component values, finite union value, and support ledger all remain
visible $\MeasureUp$ root rows.
\end{proof}

\begin{theorem}[Measure root finite disjoint additivity]
\label{thm:measure-root-finite-disjoint-additivity}
For every envelope of
\autoref{def:measure-root-finite-disjoint-envelope}, the displayed finite
union value is classified by the finite $\RealUp$ fold of the component
values:
$$
\mu(U_n)\sim_R\mathsf{fold}_R(\mu(E_0),\ldots,\mu(E_{n-1})).
$$
The classification is read from the countable-additivity row, the
finite-support empty-tail readback, and the finite disjoint-union additivity
packages already exposed by the $\MeasureUp$ root.
\end{theorem}
\begin{proof}
Embed the finite family into a countable family by appending the constant
empty tail named in the support-ledger field of the envelope. The carrier
part of \autoref{thm:measure-root-finite-disjoint-carrier-classifier} keeps
the finite spine, the empty tail, and the displayed union in the same
$\mathsf{BHist}$ ledger.

Apply \autoref{thm:measure-root-public-obligation-basis-additivity}. It
supplies the countable disjoint-additivity row, the finite readback row, and
the countable-sum classifier transport over the visible ledger.

The empty tail is read by
\autoref{thm:measure-root-finite-support-additivity-readback} and
\autoref{thm:measure-finite-support-countable-readback}. These rows identify
the countable endpoint of the finite-support family with the finite
$\RealUp$ fold of the displayed component endpoints.

It remains to compare the displayed finite union endpoint with that finite
fold. Use \autoref{thm:measure-finite-disjoint-union-additivity} along the
finite union tree, with additive congruence and associativity from the
$\RealUp$ $\AbGroupUp$ row. Composing these classifier comparisons gives the
displayed readback for $\mu(U_n)$.
\end{proof}

\begin{theorem}[Measure root finite disjoint consumer threshold]
\label{thm:measure-root-finite-disjoint-consumer-threshold}
The downstream $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$ consumers of a
\autoref{def:measure-root-finite-disjoint-envelope} may read exactly the
event carrier, displayed finite union, $\RealUp$ value fold, and
finite-support ledger rows of the envelope. They receive no
sigma-completeness row, open-cover compactness row, standard bridge row,
quotient event equality, host set equality, or analytic completion object
from this package.
\end{theorem}
\begin{proof}
Begin with the consumer boundary field of
\autoref{def:measure-root-finite-disjoint-envelope}. It names only the
carrier, finite union, value fold, and finite-support ledger rows as outgoing
analysis data.

For the shared carrier and endpoint rows, apply
\autoref{thm:measure-root-finite-disjoint-carrier-classifier}. This pins
every consumer-visible event and value to the root $\mathsf{BHist}$ ledger
and the $\RealUp$ endpoint classifier.

For the finite value readback, apply
\autoref{thm:measure-root-finite-disjoint-additivity}. The downstream
consumers see the displayed union value only through the finite fold
comparison supplied by the envelope.

Now project the three consumer faces through
\autoref{thm:measure-root-finite-support-downstream-exhaustion},
\autoref{thm:measure-integral-consumer-rows},
\autoref{thm:measure-probability-consumer-rows}, and
\autoref{thm:measure-functionalanalysis-consumer-rows}. These projections
read finite-support rows from the same root package and do not add a fourth
consumer or a broader analytic interface.

The excluded-surface field of the envelope contains no slot for
sigma-completeness, open-cover compactness, quotient event equality, host set
equality, analytic completion, or $\StdBridge$ data. Therefore the three
analysis consumers receive exactly the four named row families and no larger
surface.
\end{proof}
