\begin{definition}[Measure root analysis-unblock obligation surface]
\label{def:measure-root-analysis-unblock-obligation-surface}
The $\MeasureUp$ root analysis-unblock obligation surface is the ten-row
template obtained by reading the analysis-unblock source of
\autoref{def:measure-analysis-unblock-source}, the root public NameCert
surface of \autoref{def:measure-root-namecert-public-surface}, and the
analysis-seed source of \autoref{def:measure-analysis-seed-source} as one
public package. Its rows are:
\begin{enumerate}
  \item the $\MeasureUp$ carrier over $\mathsf{BHist}$;
  \item the public $\hsame$ classifier for measurable-event rows;
  \item the $\RealUp$ endpoint classifier supplied by $\NameCert_{\RealUp}$;
  \item the visible event-row coverage predicate;
  \item the countable endpoint and countable-sum stability rows;
  \item finite disjoint-union additivity;
  \item relative-difference additivity for displayed inclusions;
  \item monotone inclusion and nonnegative $\RealUp$ value rows;
  \item continuity from below for displayed increasing measurable sequences;
  \item the ledger and downstream exactness rows consumed by $\IntegralUp$,
  $\ProbSpaceUp$, and $\FunctionalAnalysisUp$.
\end{enumerate}
\end{definition}

\begin{theorem}[Measure root analysis-unblock carrier-classifier]
\label{thm:measure-root-analysis-unblock-carrier-classifier}
The surface of
\autoref{def:measure-root-analysis-unblock-obligation-surface} supplies the
$\MeasureUp$ carrier, the public measurable-event classifier, event-row
coverage, and countable endpoint stability rows. These are precisely the
carrier-classifier rows exposed by the root public NameCert surface and read
by the analysis-unblock source.
\end{theorem}
\begin{proof}
Project the carrier, classifier, event-row coverage, ledger, and endpoint
rows from \autoref{def:measure-root-namecert-public-surface}. Apply
\autoref{thm:measure-root-carrier-classifier-public-obligation} to transport
the carrier code, every visible event row, every ledger row, and every
$\RealUp$ endpoint row along the public classifier.

Next read the same projections through
\autoref{def:measure-analysis-unblock-source}. Apply
\autoref{thm:measure-analysis-unblock-carrier-classifier-scope}. It
identifies the analysis-unblock carrier, public classifier, event-row
coverage, and countable-sum endpoint stability rows with the rows already
projected from the root public surface.

Repack these common projections in the ten-row template of
\autoref{def:measure-root-analysis-unblock-obligation-surface}. The repacked
surface contains no additional host equality, quotient event equality, or
standard bridge row, so the carrier-classifier package is the stated public
one.
\end{proof}

\begin{theorem}[Measure root analysis-unblock additivity-continuity]
\label{thm:measure-root-analysis-unblock-additivity-continuity}
The surface of
\autoref{def:measure-root-analysis-unblock-obligation-surface} packages
finite disjoint-union additivity, relative-difference additivity, monotone
inclusion, nonnegative $\RealUp$ values, and continuity from below for
displayed increasing measurable sequences.
\end{theorem}
\begin{proof}
First project the finite rows from the public $\MeasureUp$ package. Apply
\autoref{thm:measure-two-step-finite-additivity-package}; its two-step
readback supplies the finite disjoint-union additive row used by the root
analysis-unblock surface.

Next project the relative and order rows through
\autoref{thm:measure-analysis-unblock-relative-continuity-package}. This
single package supplies relative-difference additivity, monotone inclusion,
and nonnegative $\RealUp$ values over the same carrier and endpoint
classifier.

For countable increasing sequences, apply
\autoref{thm:measure-continuity-from-below-package}. Its construction uses
the same visible event rows, relative-difference rows, finite readbacks,
countable-sum classifier stability, and $\RealUp$ endpoint classifier as the
root surface.

The rows cited above are all rows of the ten-row template in
\autoref{def:measure-root-analysis-unblock-obligation-surface}. Repacking
them gives one additivity-continuity package and adds no extra equality or
standard-bridge assumption.
\end{proof}

\begin{theorem}[Measure root analysis-unblock downstream package]
\label{thm:measure-root-analysis-unblock-downstream-package}
The surface of
\autoref{def:measure-root-analysis-unblock-obligation-surface} is the
$\MeasureUp$ package consumed by $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$. The consumer boundary consists only of the carrier,
classifier, stability, exactness, ledger, additivity, order, endpoint, and
continuity rows named in that surface.
\end{theorem}
\begin{proof}
Apply \autoref{thm:measure-analysis-unblock-downstream-source}. It assembles
the integral premeasure rows, the probability normalization rows, and the
functional-analysis endpoint and order rows from the public $\MeasureUp$
analysis substrate.

Read that assembled source through the ten-row surface of
\autoref{def:measure-root-analysis-unblock-obligation-surface}. The
$\IntegralUp$ consumer sees the measurable-event, endpoint, finite-readback,
and countable-sum rows; the $\ProbSpaceUp$ consumer sees the total-event,
unit-mass, empty-zero, and finite-additivity rows; the
$\FunctionalAnalysisUp$ consumer sees the nonnegative, monotone,
relative-difference, and countable-stability rows.

The exactness and ledger rows of the surface keep the three downstream fronts
inside the displayed $\MeasureUp$ package. Therefore the root
analysis-unblock surface is the paper-side package consumed by those fronts
and carries no additional standard bridge row.
\end{proof}
