\begin{definition}[Measure root BHist NameCert input packet]
\label{def:measure-root-bhist-namecert-input-packet}
The $\MeasureUp$ root $\mathsf{BHist}$ $\NameCert$ input packet is the
ten-field public packet whose fields are:
\begin{enumerate}
  \item the source carrier $\mathsf{BHist}$;
  \item the componentwise history classifier $\hsame$;
  \item the continuation row $\Cont$ used to preserve displayed root
  histories;
  \item the $\NameCert_{\RealUp}$ endpoint certificate;
  \item the additive $\AbGroupUp$ real row for endpoint sums and differences;
  \item the $\StreamNameUp$ countable-family name rows;
  \item the displayed measurable-event carrier and classifier rows of the
  root $\MeasureUp$ ledger;
  \item the empty-zero, finite disjoint-union, countable-disjoint-additivity,
  relative-difference, and continuity-from-below rows read from the same
  ledger;
  \item the consumer boundary rows for $\IntegralUp$, $\ProbSpaceUp$, and
  $\FunctionalAnalysisUp$;
  \item the exclusion row stating that no quotient event equality, host set
  equality, standard bridge row, or open-cover compactness row is part of the
  packet.
\end{enumerate}
Thus the packet is a single $\mathsf{BHist}$-facing input surface for the
root measure certificate and its three displayed downstream consumers.
\end{definition}

\begin{theorem}[Measure root BHist input carrier-classifier]
\label{thm:measure-root-bhist-input-carrier-classifier}
The packet of
\autoref{def:measure-root-bhist-namecert-input-packet} supplies exactly the
carrier and classifier transport required by the root $\MeasureUp$ domain:
displayed $\mathsf{BHist}$ event carriers, componentwise $\hsame$ classifier
movement, $\Cont$ preservation of root histories, $\StreamNameUp$
countable-family transport, and $\NameCert_{\RealUp}$ endpoint transport.
No downstream consumer row is needed to obtain this carrier-classifier face.
\end{theorem}
\begin{proof}
Start with the source carrier, classifier, continuation, endpoint, additive,
countable-family, and displayed ledger fields of
\autoref{def:measure-root-bhist-namecert-input-packet}. These fields are all
root-facing input rows, so the carrier-classifier face can be read before any
consumer projection is used.

Apply \autoref{thm:measure-bhist-root-carrier-obligation}. It places every
accepted event row on a displayed $\mathsf{BHist}$ carrier with its
$\StreamNameUp$ observation row and $\RealUp$ endpoint witnesses.

Apply \autoref{thm:measure-bhist-root-classifier-obligation}. This identifies
the classifier transport as componentwise $\hsame$ movement of histories,
pointwise $\StreamNameUp$ transport, and $\RealUp$ endpoint classifier
transport, with no host set equality or quotient event equality.

Finally apply \autoref{thm:measure-root-domain-carrier-classifier-ready}. The
domain-ready package repacks those same rows with $\Cont$,
$\NameCert_{\RealUp}$, the additive $\AbGroupUp$ real row, and the
$\StreamNameUp$ countable-family names. Hence the packet supplies exactly the
carrier-classifier transport stated above.
\end{proof}

\begin{theorem}[Measure root BHist input countable additivity]
\label{thm:measure-root-bhist-input-countable-additivity}
The packet of
\autoref{def:measure-root-bhist-namecert-input-packet} supplies the
empty-zero row, finite disjoint-union readback, countable-disjoint additivity,
relative-difference additivity, and continuity-from-below row for the root
$\MeasureUp$ ledger. These rows are read on displayed $\mathsf{BHist}$ event
families with $\StreamNameUp$ names and $\NameCert_{\RealUp}$ endpoint sums.
\end{theorem}
\begin{proof}
Project the additivity field of
\autoref{def:measure-root-bhist-namecert-input-packet}. It contains the
empty event, finite disjoint unions, covered pairwise-disjoint countable
families, relative differences, increasing chains, $\RealUp$ endpoint
comparisons, additive real rows, and visible ledger witnesses.

Apply \autoref{thm:measure-root-public-countable-additivity-threshold}. It
gives the countable-disjoint comparison for covered measurable sequences,
and it reads the empty-zero and finite disjoint-union rows from the same
public threshold package.

Next apply \autoref{thm:measure-root-domain-sigma-additive-ready}. This
places sigma-additivity, empty-zero, finite disjoint-union readback,
finite-support countable readback, relative-difference additivity, and
continuity from below on the domain-ready root package.

Finally apply \autoref{thm:measure-bhist-root-ledger-obligation}. The ledger
obligation pins these witnesses to displayed $\mathsf{BHist}$ event rows,
countable-family rows, disjointness rows, countable-union rows, endpoint
witnesses, and countable-sum rows. Repacking the three cited sources gives
exactly the countable-additivity face of the packet.
\end{proof}

\begin{theorem}[Measure root BHist input consumer exactness]
\label{thm:measure-root-bhist-input-consumer-exactness}
The packet of
\autoref{def:measure-root-bhist-namecert-input-packet} is exactly the root
$\MeasureUp$ surface consumed by $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$. The consumers read the displayed carrier-classifier,
endpoint, additivity, relative-difference, and continuity rows of the packet;
they do not consume quotient event equality, host set equality, standard
bridge rows, or open-cover compactness rows.
\end{theorem}
\begin{proof}
Begin with the consumer boundary and exclusion fields of
\autoref{def:measure-root-bhist-namecert-input-packet}. The boundary names
only the $\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ rows, while
the exclusion row removes quotient event equality, host set equality,
standard bridge data, and open-cover compactness data from the input surface.

Apply \autoref{thm:measure-root-domain-downstream-ready}. It reads the
carrier-classifier and sigma-additive rows as exactly the rows consumed by the
three downstream faces, with no quotient event equality, no host set equality,
and no standard bridge row.

Apply \autoref{thm:measure-root-consumer-boundary-threshold}. This identifies
the $\IntegralUp$ boundary, the $\ProbSpaceUp$ normalization boundary, and the
$\FunctionalAnalysisUp$ nonnegative, monotone, relative-difference, and
countable-sum boundary as the shared root surface and nothing beyond it.

Finally apply
\autoref{thm:measure-root-visible-shared-consumer-deps-ready}. Its
deps-ready package exports only visible event rows, endpoint classifier rows,
endpoint-family rows, continuation rows, and displayed ledger witnesses to
the same consumers. Combining these projections proves that the packet is the
exact consumer input surface and that the four excluded row classes are not
consumed.
\end{proof}
