\begin{definition}[Measure root minimum NameCert obligation triad]
\label{def:measure-root-minimum-namecert-obligation-triad}
The $\MeasureUp$ root minimum $\NameCert$ obligation triad is the
three-field root package read from $\mathsf{BHist}$ presentations, the
componentwise $\hsame$ classifier, $\NameCert_{\RealUp}$ endpoint transport,
and $\StreamNameUp$ countable-family rows:
\begin{enumerate}
  \item carrier-classifier field: the measurable-event carrier
  $\mathsf{MeasCode}$, the public classifier $\sim_M$, visible event-row
  transport, endpoint transport through $\NameCert_{\RealUp}$, and carrier
  transport along componentwise $\hsame$;
  \item countable-additivity field: StreamName-indexed measurable sequence
  coverage, pairwise-disjoint and countable-union readback, countable-sum
  endpoint rows, and the $\RealUp$ comparison between the value of the union
  and the displayed countable endpoint;
  \item downstream ledger field: the rows available to $\IntegralUp$,
  $\ProbSpaceUp$, and $\FunctionalAnalysisUp$, namely the
  carrier/classifier rows, countable-additivity rows, nonnegative endpoint
  rows, and ledger rows attached to visible measurable-event witnesses.
\end{enumerate}
The triad is a minimum public root surface: it contains no host set equality,
no quotient equality of event codes, no analytic completion object, and no
open-cover compactness row.
\end{definition}

\begin{theorem}[Measure root minimum carrier-classifier obligation]
\label{thm:measure-root-minimum-carrier-classifier-obligation}
The triad of
\autoref{def:measure-root-minimum-namecert-obligation-triad} supplies the
$\MeasureUp$ root carrier predicate, public classifier, and carrier transport
only through the displayed BEDC rows of
\autoref{def:measureup-carrier-obligation-inventory},
\autoref{def:measure-classifier-specification},
\autoref{thm:measure-root-namecert-carrier-classifier},
\autoref{thm:measure-root-namecert-stability-exactness}, and
\autoref{def:measure-root-public-obligation-basis}.
\end{theorem}
\begin{proof}
Read the first field of
\autoref{def:measure-root-minimum-namecert-obligation-triad}. Its carrier is
the $\mathsf{BHist}$ measurable-event carrier and its classifier is the
componentwise $\hsame$ relation with endpoint motion read through
$\NameCert_{\RealUp}$.

The inventory in \autoref{def:measureup-carrier-obligation-inventory} names
exactly those carrier, classifier, stability, and ledger rows. The classifier
specification in \autoref{def:measure-classifier-specification} then restricts
comparison to event-witness transport and $\RealUp$ endpoint comparison.

Apply \autoref{thm:measure-root-namecert-carrier-classifier} and
\autoref{thm:measure-root-namecert-stability-exactness}. They identify the
root $\NameCert_{\MeasureUp}$ carrier, classifier, and stability face with the
displayed event, endpoint, and ledger rows.

Finally compare with
\autoref{def:measure-root-public-obligation-basis}. Its carrier and
classifier fields expose the same rows and no larger equality principle.
Thus the triad supplies the root carrier-classifier obligation only through
the displayed BEDC rows.
\end{proof}

\begin{theorem}[Measure root minimum countable-additivity obligation]
\label{thm:measure-root-minimum-countable-additivity-obligation}
The triad of
\autoref{def:measure-root-minimum-namecert-obligation-triad} supplies
measurable-sequence coverage, disjoint-union readback, and
$\RealUp$ endpoint comparison for the $\MeasureUp$ countable-additivity row.
Every countable family consumed by this row is read through
$\StreamNameUp$, componentwise $\hsame$, and the public ledger of
\autoref{def:measure-root-public-obligation-basis}.
\end{theorem}
\begin{proof}
Project the second field of
\autoref{def:measure-root-minimum-namecert-obligation-triad}. It names the
StreamName-indexed measurable family, the pairwise-disjoint witness, the
countable union row, the countable-sum endpoint, and the $\RealUp$ comparison
attached to that endpoint.

The carrier inventory of
\autoref{def:measureup-carrier-obligation-inventory} supplies the measurable
sequence, disjointness, union, and countable-sum ledger rows. The classifier
specification of \autoref{def:measure-classifier-specification} keeps their
movement componentwise, with endpoint motion through
$\NameCert_{\RealUp}$.

Apply \autoref{thm:measure-root-namecert-stability-exactness}. Its
countable-endpoint and $\sigma$-additivity projections supply the stated
comparison between the value of the visible disjoint union and the displayed
countable endpoint.

The public basis of
\autoref{def:measure-root-public-obligation-basis} records these rows as the
root additive face. Therefore the triad contains the countable-additivity
obligation exactly as measurable-sequence coverage, disjoint-union readback,
and $\RealUp$ endpoint comparison.
\end{proof}

\begin{theorem}[Measure root minimum downstream consumer obligation]
\label{thm:measure-root-minimum-downstream-consumer-obligation}
The triad of
\autoref{def:measure-root-minimum-namecert-obligation-triad} permits
$\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ to consume exactly
the carrier/classifier rows, countable-additivity rows, nonnegative endpoint
rows, and ledger rows displayed by the $\MeasureUp$ root. It exports no host
set equality, no quotient equality, and no open-cover compactness.
\end{theorem}
\begin{proof}
Read the downstream ledger field of
\autoref{def:measure-root-minimum-namecert-obligation-triad}. It names only
the three consumers $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$ and restricts their input to carrier/classifier,
countable-additivity, nonnegative endpoint, and visible ledger rows.

The root carrier inventory and classifier specification provide the common
input rows for all three consumers. The root NameCert carrier-classifier and
stability-exactness theorems identify these rows with the public
$\MeasureUp$ root face.

Apply \autoref{def:measure-root-public-obligation-basis}. Its consumer and
exactness fields attach every downstream witness to displayed
measurable-event, endpoint, disjointness, relative-difference, and
countable-sum rows.

Since none of those cited rows contains a host set equality field, quotient
event equality field, or open-cover compactness field, the triad exports
exactly the downstream consumer obligation stated above.
\end{proof}
