\begin{theorem}[Measure root NameCert carrier and classifier]
\label{thm:measure-root-namecert-carrier-classifier}
The root $\NameCert_{\MeasureUp}$ surface has carrier face
$\mathsf{MeasCode}$ and classifier face $\sim_M$ exactly as displayed in
\autoref{def:measure-sigma-algebra-carrier-surface} and
\autoref{def:measure-certificate-surface}. Its visible event rows are the
empty-event, binary-union, countable-union, complement/relative-difference,
disjoint-sequence readback, and countable-sum endpoint rows of those
definitions, and its endpoint classifier rows are read through the
$\RealUp$ classifier $\sim_R$. The root face does not assert a quotient of
measure codes and does not identify host event predicates by ambient set
equality.
\end{theorem}
\begin{proof}
Project the carrier list of
\autoref{def:measure-sigma-algebra-carrier-surface}. The third, fourth, fifth,
sixth, and eighth fields name the displayed measure-code carrier, the
componentwise classifier, the event-row stability data, the ledger rows, and
the visible-row exactness requirement.

Next project \autoref{def:measure-certificate-surface}. Its first two clauses
name $\mathsf{MeasCode}$, $\sim_M$, and the core
$\NameCert(\mathsf{MeasCode},\sim_M)$ transport field. Its event-family,
endpoint, countable-sum, $\sigma$-algebra, $\sigma$-additivity, head-tail, and
countable-sum classifier clauses supply the visible rows and the $\RealUp$
endpoint classifier.

The statement follows by reading these projections as the root public face:
transport is the $\NameCert$ transport field, while quotienting of codes and
ambient host set equality never appear among the displayed fields.
\end{proof}

\begin{theorem}[Measure root NameCert stability and exactness]
\label{thm:measure-root-namecert-stability-exactness}
For the root $\NameCert_{\MeasureUp}$ surface,
\autoref{thm:measure-carrier-classifier-obligation},
\autoref{thm:measure-obligation-countable-sum-classifier-stability},
\autoref{thm:measure-sigma-additivity-obligation}, and
\autoref{thm:measure-ledger-exactness-obligation} supply, respectively,
componentwise transport of the carrier rows, classifier stability of
countable-sum endpoints, $\sigma$-additive classification of disjoint
countable unions, and visible ledger exhaustion for every witness consumed by
the root surface.
\end{theorem}
\begin{proof}
Start with \autoref{thm:measure-carrier-classifier-obligation}. It transports
the displayed empty, binary-union, countable-union,
complement/relative-difference, disjoint-readback, and endpoint rows
componentwise along the public $\MeasureUp$ classifier.

The countable endpoint row is stable by
\autoref{thm:measure-obligation-countable-sum-classifier-stability}. This
keeps the $\RealUp$ endpoint classifier compatible with pointwise transport of
measurable sequences.

The $\sigma$-additive classifier row is supplied by
\autoref{thm:measure-sigma-additivity-obligation}: pairwise-disjoint
measurable sequences with displayed union $U$ classify $\mu(U)$ against the
countable endpoint assigned to the sequence.

Finally \autoref{thm:measure-ledger-exactness-obligation} states that the
membership, relative-difference, disjointness, value, and countable-sum
witnesses consumed by the surface are exactly the witnesses attached to the
visible rows. These four rows therefore give the stability and exactness face
of the root package.
\end{proof}

\begin{theorem}[Measure root downstream boundary]
\label{thm:measure-root-namecert-downstream-boundary}
The downstream public boundary of the root $\NameCert_{\MeasureUp}$ surface is
exactly the collection exposed by
\autoref{thm:measure-namecert-obligation-package},
\autoref{thm:measure-probability-normalization-row}, and
\autoref{thm:measure-integral-premeasure-consumption}. These are precisely the
rows consumed by $\ProbSpaceUp$, $\IntegralUp$, and
$\FunctionalAnalysisUp$, with no additional host carrier, quotient relation, or
unlisted ledger witness exported to those chapters.
\end{theorem}
\begin{proof}
Project \autoref{thm:measure-namecert-obligation-package}. It packages the
carrier, classifier, stability, exactness, nonnegative value, monotone
inclusion, and measure consequence rows as the public $\MeasureUp$ substrate.

The probability boundary is the one isolated by
\autoref{thm:measure-probability-normalization-row}. It exposes the total
event normalization and the finite-additivity rows used by $\ProbSpaceUp$,
while keeping the remaining measure witnesses inside the named package.

The integral and functional-analysis boundary is the one isolated by
\autoref{thm:measure-integral-premeasure-consumption}. It exposes measurable
event membership, nonnegative endpoints, monotone inclusion,
relative-difference rows, and countable-sum rows to $\IntegralUp$ and
$\FunctionalAnalysisUp$. Together these projections give exactly the
downstream boundary stated above.
\end{proof}
