\begin{definition}[Measure root dependency orientation surface]
\label{def:measure-root-dependency-orientation-surface}
The $\MeasureUp$ root dependency orientation surface is the root
$\mathsf{BHist}$ package whose carrier is $\mathsf{MCarrier}$ and whose
classifier is the componentwise $\MeasureUp$ classifier transported by
$\hsame$. Its sequence rows are indexed only by unary observations
$n:\mathsf{BHist}$ with $\mathsf{UnaryHistory}(n)$, and its continuation rows
are the $\Cont$ rows used to keep event presentations, relative-difference
witnesses, countable-union witnesses, and countable-sum endpoints in the same
visible ledger.

The input certificates of the surface are exactly the following rows:
\begin{enumerate}
  \item $\NameCert_{\RealUp}$ for displayed endpoint classifiers, zero
  endpoints, order comparisons, and countable-sum endpoint comparisons;
  \item the additive real rows already named by
  \autoref{def:measure-sigma-algebra-carrier-surface} and
  \autoref{def:measure-root-namecert-public-surface};
  \item $\NameCert_{\StreamNameUp}$ only where the endpoint-family rows of
  \autoref{def:measure-streamname-endpoint-family} are used.
\end{enumerate}
No row from $\IntegralUp$, $\ProbSpaceUp$, or $\FunctionalAnalysisUp$ is an
input certificate for this root surface. Those objects are reachable only
through the downstream consumer package.
\end{definition}

\begin{theorem}[Measure root input dependency scope]
\label{thm:measure-root-input-dependency-scope}
The carrier, classifier, event coverage, finite additivity,
sigma-additivity, continuity-from-below, and endpoint-family rows of
$\MeasureUp$ are proved from the orientation surface of
\autoref{def:measure-root-dependency-orientation-surface}, the BEDC kernel
constructs $\mathsf{BHist}$, $\hsame$, and $\Cont$, the named
$\NameCert_{\RealUp}$ and additive real rows, and the
$\NameCert_{\StreamNameUp}$ rows at endpoint-family sites. They are not
proved from any $\IntegralUp$, $\ProbSpaceUp$, or $\FunctionalAnalysisUp$
consumer row.
\end{theorem}
\begin{proof}
Project the carrier and classifier rows from
\autoref{thm:measure-root-namecert-carrier-classifier}. The carrier is the
displayed $\mathsf{MCarrier}$ row over $\mathsf{BHist}$, and classifier
movement is the componentwise $\hsame$ transport built into the root
NameCert surface.

Next apply \autoref{thm:measure-root-namecert-stability-exactness}. Its
stability and exactness projections say that every visible event witness,
relative-difference witness, countable-union witness, and endpoint witness is
read from the displayed ledger and transported only through the root
classifier, $\Cont$, and the $\RealUp$ endpoint classifier.

The finite-additivity, sigma-additivity, and continuity-from-below rows are
then read through the public additive and countable-sum rows cited by the
measure surface. Endpoint-family rows use
\autoref{def:measure-streamname-endpoint-family}, so the only extra
certificate at those sites is $\NameCert_{\StreamNameUp}$.

Finally compare the resulting root package with
\autoref{thm:measure-root-downstream-unblock-package}. That theorem exports
rows from $\MeasureUp$ to the three downstream consumers; it does not import
consumer rows back into the carrier, classifier, additivity, continuity, or
endpoint-family obligations. Hence the listed root obligations have precisely
the input scope stated above.
\end{proof}

\begin{theorem}[Measure root consumer projection separation]
\label{thm:measure-root-consumer-projection-separation}
The $\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ rows exposed in
\autoref{def:measure-root-consumer-package} are projections out of the root
$\MeasureUp$ package. They cannot be used as hypotheses for the root carrier,
classifier, event-coverage, additivity, continuity-from-below, or
endpoint-family obligations of $\MeasureUp$.
\end{theorem}
\begin{proof}
Start with \autoref{def:measure-root-consumer-package}. The definition reads
the root NameCert public surface together with the downstream package of
\autoref{thm:measure-root-downstream-unblock-package}; its consumer rows are
therefore projections from an already assembled root surface.

For the three consumers, apply
\autoref{thm:measure-root-downstream-unblock-package}. The integral face
receives measurable-event, endpoint, countable-sum, head-tail, and finite
readback rows; the probability face receives total-event normalization,
empty-zero, and finite-additivity rows; the functional-analysis face receives
nonnegative endpoint, monotone inclusion, relative-difference, and
countable-sum classifier rows.

Now return to the root obligations named in
\autoref{def:measure-root-dependency-orientation-surface}. Their hypotheses
are $\mathsf{BHist}$, $\hsame$, $\Cont$, $\NameCert_{\RealUp}$, the additive
real rows, and endpoint-family $\NameCert_{\StreamNameUp}$ rows. None of the
three consumer projections appears among those hypotheses.

The exactness row of \autoref{def:measure-root-consumer-package} keeps the
consumer boundary one-way: downstream rows may cite the root package, but
root proof obligations cite only the orientation surface and its named input
certificates. This separates the projections from the hypotheses used to
build $\MeasureUp$.
\end{proof}

\begin{theorem}[Measure root deps-ready public package]
\label{thm:measure-root-deps-ready-public-package}
The orientation surface of
\autoref{def:measure-root-dependency-orientation-surface} together with the
threshold package of \autoref{def:measure-root-bhist-consumer-threshold}
forms the public deps-ready $\MeasureUp$ package for $\IntegralUp$,
$\ProbSpaceUp$, and $\FunctionalAnalysisUp$. This package exposes exactly the
root $\mathsf{BHist}$ carrier and classifier rows, $\RealUp$ endpoint rows,
additive and continuity rows, endpoint-family rows, the downstream consumer
projections, and the no-$\StdBridge$ boundary recorded by the threshold.
\end{theorem}
\begin{proof}
Use \autoref{def:measure-root-dependency-orientation-surface} to fix the root
input face. It supplies the carrier orientation over $\mathsf{BHist}$,
classifier transport by $\hsame$, continuation discipline through $\Cont$,
and the only external certificates allowed at root input sites.

Apply \autoref{thm:measure-root-input-dependency-scope}. This proves that the
root carrier, classifier, coverage, additivity, continuity-from-below, and
endpoint-family rows are obtained before any downstream consumer projection is
used.

Next combine those rows with
\autoref{def:measure-root-bhist-consumer-threshold}. The threshold package
lists the visible event ledger, endpoint comparisons, additive rows,
exactness row, and the three downstream consumer faces, while excluding host
set equality, quotient event equality, analytic completion objects, and
standard bridges.

Finally apply
\autoref{thm:measure-root-consumer-projection-separation}. It identifies the
consumer faces as outgoing projections only. Repacking the input face and the
threshold face therefore gives a public deps-ready package that downstream
analysis chapters may consume without using those chapters to justify the
root $\MeasureUp$ obligations.
\end{proof}
