\section{Measure root finite-support consumer front}
\label{sec:measure-root-finite-support-consumer-front}

\begin{definition}[Measure root finite-support consumer front]
\label{def:measure-root-finite-support-consumer-front}
The $\MeasureUp$ root finite-support consumer front is the ten-field package
that exposes the finite-support rows needed by downstream analysis consumers:
\begin{enumerate}
  \item traditional target: finite-support measurable events with readback
  values in the $\RealUp$ additive endpoint surface;
  \item BEDC source: $\MeasureUp+\StreamNameUp+\RealUp+\AbGroupUp$;
  \item carrier: a covered finite support spine of displayed measurable
  $\mathsf{BHist}$ event rows together with a constant empty tail;
  \item classifier: the public $\MeasureUp$ event classifier together with
  the $\RealUp$ endpoint classifier for each displayed value and finite sum;
  \item stability: componentwise event transport, endpoint transport,
  additive congruence, and support-spine transport;
  \item ledger: the finite support spine, the constant empty tail, the
  countable-union row, and the finite union tree read from the same displayed
  $\mathsf{BHist}$ rows;
  \item exactness: finite-support sum readback through
  \autoref{thm:measure-finite-support-countable-readback};
  \item displayed classification iff: a consumer row belongs to the front
  exactly when it is read from the covered event spine, the empty tail, the
  finite union tree, and the $\RealUp$ finite-sum endpoint;
  \item consumer boundary: $\IntegralUp$, $\ProbSpaceUp$, and
  $\FunctionalAnalysisUp$ may consume only the rows named in
  \autoref{thm:measure-root-finite-support-downstream-exhaustion};
  \item standard bridge: no host set equality, quotient event equality,
  $\RealUp$ completeness row, or $\StdBridge$ row is part of this front.
\end{enumerate}
The front is a finite-support face of the root consumer package of
\autoref{def:measure-root-consumer-package}, not a separate analytic
completion object.
\end{definition}

\begin{theorem}[Measure root finite-support carrier readback]
\label{thm:measure-root-finite-support-carrier-readback}
The front of \autoref{def:measure-root-finite-support-consumer-front}
supplies covered measurable-event rows and empty-tail stream rows from
\autoref{def:measure-event-row-coverage},
\autoref{thm:measure-countable-name-carrier-classifier-obligation}, and
\autoref{thm:measure-finite-support-countable-readback}. In particular, every
finite support spine visible to the front is a $\mathsf{BHist}$ event ledger
row whose constant empty tail is classified by the public $\MeasureUp$
carrier and the $\RealUp$ endpoint classifier.
\end{theorem}
\begin{proof}
Start with \autoref{def:measure-event-row-coverage}. It places the displayed
measurable events, the empty event, finite union rows, countable union rows,
and measure endpoints on visible $\mathsf{BHist}$ ledger entries.

Next apply \autoref{thm:measure-countable-name-carrier-classifier-obligation}.
The countable name carrier supplies the stream-indexed family in which the
finite support spine is followed by the constant empty tail, and it transports
the displayed event rows through the same componentwise classifier.

Finally use \autoref{thm:measure-finite-support-countable-readback}. Its
finite-support hypothesis identifies the nonempty spine and the empty tail as
one countable family, so the front reads the carrier, tail, and endpoint rows
without adding a host-level equality or quotient event comparison.
\end{proof}

\begin{theorem}[Measure root finite-support additivity readback]
\label{thm:measure-root-finite-support-additivity-readback}
For every pairwise-disjoint finite support spine exposed by
\autoref{def:measure-root-finite-support-consumer-front}, the measure of the
displayed finite union reads back to the $\RealUp$ finite sum of the displayed
support values. The readback is obtained by induction on the support spine
using the empty-zero row, finite disjoint-union additivity, and countable
empty-tail readback.
\end{theorem}
\begin{proof}
The base case is the empty support spine. The constant empty stream has empty
countable union, and
\autoref{thm:measure-empty-set-zero-from-sigma-additivity} classifies its
measure endpoint with the additive zero in the $\RealUp$ $\AbGroupUp$ row.

For the induction step, split a nonempty support spine into its head event and
tail spine. Pairwise disjointness gives the displayed binary union row between
the head and the finite union of the tail, while the induction hypothesis
reads the tail union as the finite sum of the tail values.

Apply \autoref{thm:measure-finite-disjoint-union-additivity} to the head and
tail union. Additive congruence in the $\RealUp$ $\AbGroupUp$ row transports
the tail readback through the right summand, and associativity identifies the
result with the finite sum of the whole spine.

The empty tail of the surrounding countable stream is handled by
\autoref{thm:measure-finite-support-countable-readback}. Thus the finite
union endpoint and the countable family endpoint agree with the same
$\RealUp$ finite-support sum.
\end{proof}

\begin{theorem}[Measure root finite-support downstream exhaustion]
\label{thm:measure-root-finite-support-downstream-exhaustion}
$\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ consume exactly the
finite-support rows of
\autoref{def:measure-root-finite-support-consumer-front} through
\autoref{def:measure-root-consumer-package},
\autoref{thm:measure-integral-consumer-rows},
\autoref{thm:measure-probability-consumer-rows}, and
\autoref{thm:measure-functionalanalysis-consumer-rows}. No downstream face
receives host set equality, quotient event equality, a $\RealUp$ completeness
row, or a standard bridge row from this front.
\end{theorem}
\begin{proof}
Begin with \autoref{def:measure-root-consumer-package}. Its outgoing rows are
the root $\MeasureUp$ consumer rows built from covered events, endpoint
classification, countable sums, head-tail readback, empty-zero, finite
disjoint additivity, and relative-difference or normalization projections.

For $\IntegralUp$, apply \autoref{thm:measure-integral-consumer-rows}. The
integral face reads covered event rows, endpoint rows, countable-sum rows,
head-tail readback, and finite disjoint-union readback; the finite-support
front supplies exactly the finite spine and empty-tail rows among these.

For $\ProbSpaceUp$, apply \autoref{thm:measure-probability-consumer-rows}. Its
finite-support consumption is limited to the total-event normalization,
empty-zero, and finite disjoint-union rows already present in the root
consumer package.

For $\FunctionalAnalysisUp$, apply
\autoref{thm:measure-functionalanalysis-consumer-rows}. The functional
analysis face reads nonnegative endpoint, monotone inclusion,
relative-difference, and countable-sum classifier rows, and it uses the
finite-support front only through their covered event and finite-sum
projections.

The tenth field of
\autoref{def:measure-root-finite-support-consumer-front} excludes host set
equality, quotient event equality, $\RealUp$ completeness, and standard
bridge rows. Since each downstream theorem above is a projection of the same
root consumer package, these three faces exhaust the finite-support consumer
surface.
\end{proof}
