\begin{definition}[Measure root-kernel obligation source]
\label{def:measure-root-kernel-obligation-source}
The $\MeasureUp$ root-kernel obligation source is the counted ten-field
per-object template that records the $\mathsf{BHist}$-scoped source from
which the public root measure obligations are read:
\begin{enumerate}
  \item object code: a $\mathsf{BHist}$ row $h$ carrying the visible
  measurable-event rows of the $\MeasureUp$ ledger;
  \item classifier source: componentwise $\hsame$ on histories together with
  the induced measure classifier $\sim_M$ on visible measure rows;
  \item endpoint certificate: $\NameCert_{\RealUp}$ for every displayed
  endpoint value and the $\StreamNameUp$ rows used to name countable event
  families;
  \item carrier face: the $\mathsf{MeasCode}$ predicate on
  $\mathsf{BHist}$, read through the carrier surface and the root public
  obligation basis;
  \item event boundary: exactly the visible event rows covered by
  \autoref{def:measure-event-row-coverage} and the root event boundary
  package;
  \item additive face: empty-zero, finite readback, relative-difference,
  countable disjoint-additivity, and countable-sum rows over the same
  ledger;
  \item threshold face: the root threshold package and root threshold
  obligation package, including endpoint readback and countable-family
  transport;
  \item premeasure face: the countable premeasure front over the covered
  event rows and the additive $\AbGroupUp$ real row;
  \item downstream face: only the $\IntegralUp$, $\ProbSpaceUp$, and
  $\FunctionalAnalysisUp$ consumer rows already named in the consumer
  boundary;
  \item exclusions: no host set equality, quotient event equality, analytic
  completion object, or standard bridge row is exported by this source.
\end{enumerate}
Thus each root-kernel object is counted by a single public source over
$\mathsf{BHist}$, $\hsame$, $\NameCert_{\RealUp}$, $\StreamNameUp$, visible
event rows, and the $\MeasureUp$ ledger.
\end{definition}

\begin{theorem}[Measure root-kernel carrier-classifier obligation]
\label{thm:measure-root-kernel-carrier-classifier-obligation}
For every root-kernel object described by
\autoref{def:measure-root-kernel-obligation-source}, the source supplies the
$\MeasureUp$ carrier and classifier obligation: $\mathsf{MeasCode}$ is read
on $\mathsf{BHist}$, transported along componentwise $\hsame$ and $\sim_M$,
and all visible event, endpoint, countable-family, and ledger rows remain
attached to the transported carrier.
\end{theorem}
\begin{proof}
Start from the object code, classifier source, endpoint certificate, and
carrier face of \autoref{def:measure-root-kernel-obligation-source}. These
fields place the carrier in $\mathsf{BHist}$ and make $\hsame$,
$\NameCert_{\RealUp}$, and $\StreamNameUp$ part of the same visible ledger.

Apply \autoref{thm:measure-root-public-obligation-basis-carrier}. It
transports the carrier, classifier, event rows, endpoint rows, and
countable-family rows through the public obligation basis.

Apply \autoref{thm:measure-root-threshold-carrier-classifier-obligation}.
The root threshold package keeps the same transported rows visible at the
threshold face, including endpoint readback and countable-family transport.

Finally use \autoref{thm:measure-root-event-boundary-carrier}. The event
boundary package identifies the displayed event ledger as the whole carrier
boundary. Since the source has no host set equality or quotient event
equality field, the carrier-classifier obligation is exactly the stated
$\mathsf{BHist}$-scoped one.
\end{proof}

\begin{theorem}[Measure root-kernel additivity obligation]
\label{thm:measure-root-kernel-additivity-obligation}
For every root-kernel object described by
\autoref{def:measure-root-kernel-obligation-source}, the source supplies the
additive obligation required by the public $\MeasureUp$ root: empty-zero,
finite readback, relative-difference additivity, countable
disjoint-additivity, and countable-sum transport through
$\NameCert_{\RealUp}$, $\StreamNameUp$, and the additive $\AbGroupUp$ real
row.
\end{theorem}
\begin{proof}
Read the additive, threshold, and premeasure faces of
\autoref{def:measure-root-kernel-obligation-source}. They refer to the same
covered event rows, the same endpoint certificates, and the same
countable-family names.

Apply \autoref{thm:measure-root-public-obligation-basis-additivity}. This
gives the empty-zero, finite readback, relative-difference, countable
disjoint-additivity, and countable-sum transport rows over the public
ledger.

Apply \autoref{thm:measure-root-threshold-sigma-additive-obligation}. The
root threshold package keeps the additive rows attached to the endpoint and
countable-family boundary.

Apply \autoref{thm:measure-root-countable-premeasure-additivity-obligation}.
The countable premeasure front reads those same rows through
$\NameCert_{\RealUp}$, $\StreamNameUp$, and the additive $\AbGroupUp$ real
row. The exclusions field exports no analytic completion object, so the
additivity obligation remains a root-kernel obligation rather than a
completed measure-space assertion.
\end{proof}

\begin{theorem}[Measure root-kernel downstream consumer obligation]
\label{thm:measure-root-kernel-downstream-consumer-obligation}
For every root-kernel object described by
\autoref{def:measure-root-kernel-obligation-source}, the source exports one
downstream consumer boundary: the $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$ rows obtained from the root public obligation basis,
root threshold package, event boundary package, countable premeasure front,
and consumer rows. No fourth consumer, analytic completion object, host set
equality, quotient event equality, or standard bridge row is exported.
\end{theorem}
\begin{proof}
Begin with the downstream face of
\autoref{def:measure-root-kernel-obligation-source}. It names only
$\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ as outgoing
consumer chapters.

Apply \autoref{thm:measure-root-public-obligation-basis-consumer}. The root
public obligation basis exports exactly those three rows from the public
$\MeasureUp$ root.

Apply \autoref{thm:measure-root-event-boundary-unblock}. The event boundary
package shows that the consumer rows are attached to covered visible event
rows, endpoint rows, and countable-additivity rows.

Finally apply
\autoref{thm:measure-root-countable-premeasure-consumer-threshold}. The
countable premeasure front is the common source consumed by the same three
downstream chapters. The exclusions field and the consumer boundary together
leave no slot for a fourth consumer, analytic completion object, host set
equality, quotient event equality, or standard bridge row.
\end{proof}
