\section{Measure root public face exactness}
\label{sec:measure-root-public-face-exactness}

The public face exactness package gathers the root $\MeasureUp$ endpoint
fiber that downstream chapters cite when they need the concrete BEDC event
ledger rather than a transported analytic interface.

\begin{definition}[Measure root public face exactness]
\label{def:measure-root-public-face-exactness}
The $\MeasureUp$ root public face exactness package is the concrete endpoint
fiber over $\mathsf{BHist}$ whose carrier rows are the visible measurable
event histories, whose classifier rows are componentwise $\hsame$ rows, and
whose endpoint rows are classified through $\NameCert_{\RealUp}$ and
$\StreamNameUp$. It consists of exactly the following public rows:
\begin{enumerate}
  \item the displayed $\mathsf{BHist}$ measurable membership rows, empty
  event rows, relative-difference rows, disjointness rows, countable-union
  rows, and countable-family rows covered by
  \autoref{def:measure-event-row-coverage};
  \item the $\RealUp$ endpoint classifier rows attached to measure values,
  finite readbacks, nonnegative endpoints, total-event normalization,
  monotone inclusion, and countable sums;
  \item the minimum root $\NameCert$ carrier-classifier, countable-additivity,
  and downstream ledger fields of
  \autoref{def:measure-root-minimum-namecert-obligation-triad};
  \item the public sigma-algebra carrier, empty-zero, and countable
  disjoint-additivity rows of
  \autoref{def:measure-root-sigma-algebra-public-basis};
  \item the outgoing $\IntegralUp$, $\ProbSpaceUp$, and
  $\FunctionalAnalysisUp$ faces accepted by
  \autoref{def:measure-root-consumer-acceptance-gate}.
\end{enumerate}
This package introduces no host set equality, no quotient event equality, no
analytic completion object, and no standard bridge row.
\end{definition}

\begin{theorem}[Measure root public face coverage]
\label{thm:measure-root-public-face-coverage}
Every endpoint fiber in
\autoref{def:measure-root-public-face-exactness} is covered by the event-row
coverage predicate of \autoref{def:measure-event-row-coverage}, the minimum
root $\NameCert$ triad of
\autoref{def:measure-root-minimum-namecert-obligation-triad}, and the
sigma-algebra public basis of
\autoref{def:measure-root-sigma-algebra-public-basis}.
\end{theorem}
\begin{proof}
Start with the listed rows of
\autoref{def:measure-root-public-face-exactness}. The event side consists
only of displayed $\mathsf{BHist}$ measurable membership, empty-event,
relative-difference, disjointness, countable-union, and countable-family rows.

Apply \autoref{def:measure-event-row-coverage}. It places each event row in
the visible ledger, together with the attached measure-value and countable-sum
endpoint rows.

Next apply
\autoref{def:measure-root-minimum-namecert-obligation-triad}. Its
carrier-classifier field supplies the $\hsame$ event classifier, its
countable-additivity field supplies the $\StreamNameUp$ family and
$\RealUp$ endpoint-sum rows, and its downstream ledger field keeps those rows
visible to the three named consumers.

Finally use \autoref{def:measure-root-sigma-algebra-public-basis},
\autoref{thm:measure-root-real-stream-event-obligation}, and
\autoref{thm:measure-root-source-deps-ready-package}. The public basis gives
the carrier, empty-zero, and countable disjoint-additivity rows; the
real-stream obligation attaches StreamName observation names and endpoint
comparisons to the same event history; the source package confirms that all
source witnesses remain ledger rows rather than host equalities or analytic
completion data.
\end{proof}

\begin{theorem}[Measure root public face determinacy]
\label{thm:measure-root-public-face-determinacy}
For a displayed event row of
\autoref{def:measure-root-public-face-exactness}, the event display together
with its $\RealUp$ endpoint classifier determines one public $\MeasureUp$
endpoint fiber. The determinacy is a BEDC endpoint-fiber determinacy statement;
it is not host event equality and not quotient equality of event codes.
\end{theorem}
\begin{proof}
Fix a displayed event row in the public face. By
\autoref{def:measure-root-public-face-exactness}, the row carries a
componentwise $\hsame$ classifier and a $\RealUp$ endpoint classifier through
$\NameCert_{\RealUp}$.

Apply \autoref{thm:measure-root-event-classifier-stability}. It transports
the carried $\MeasureUp$ root row and its visible ledger along the displayed
event history, StreamName observation, and real endpoint classifier.

Now use \autoref{thm:measure-root-sigma-algebra-public-carrier} and
\autoref{thm:measure-root-real-stream-carrier-regularity}. The sigma-algebra
carrier keeps the public event row in the root carrier, while the real-stream
carrier places the observation name and endpoint comparison on that same row.

The consumer and source boundaries do not identify host events. By
\autoref{thm:measure-root-consumer-acceptance-coverage} and
\autoref{thm:measure-root-source-event-row-closure}, the accepted row remains
a visible ledger row with endpoint data attached. Thus the displayed event
and endpoint classifier determine exactly one public endpoint fiber of the
BEDC root surface, with no host set equality, quotient event equality,
analytic completion object, or standard bridge row added.
\end{proof}

\begin{theorem}[Measure root public face ledger exhaustion]
\label{thm:measure-root-public-face-ledger-exhaustion}
Every ledger entry consumed by
\autoref{def:measure-root-public-face-exactness} is a measurable membership
row, relative-difference row, disjointness row, measure-value row, or
countable-sum row supplied by
\autoref{thm:measure-ledger-exactness-obligation}. No other source witness is
part of the public endpoint fiber.
\end{theorem}
\begin{proof}
Read the ledger clause of
\autoref{def:measure-root-public-face-exactness}. It contains exactly the
visible event rows and endpoint rows listed in
\autoref{def:measure-event-row-coverage}, plus the downstream faces accepted
by the root consumer gate.

Apply \autoref{thm:measure-ledger-exactness-obligation}. Its exactness clause
exhausts the consumed source witnesses by measurable membership,
relative-difference, disjointness, measure-value, and countable-sum rows.

Next apply \autoref{thm:measure-root-source-ledger-exhaustion}. It reads the
same witness list through the source-closure package and keeps probability
normalization, integral premeasure rows, functional-analysis rows, and bridge
rows outside the source ledger.

Finally use \autoref{thm:measure-root-countable-additivity-scope} and
\autoref{thm:measure-root-consumer-acceptance-downstream-package}. The
additivity scope accounts for the $\StreamNameUp$ countable-family endpoint
rows, and the acceptance package shows that downstream consumers receive only
projections of the exhausted ledger. Therefore no host set equality, quotient
event equality, analytic completion object, or standard bridge row enters the
public endpoint fiber.
\end{proof}

\begin{theorem}[Measure root public face consumer separation]
\label{thm:measure-root-public-face-consumer-separation}
Inside the public endpoint fiber of
\autoref{def:measure-root-public-face-exactness}, the chapters
$\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ consume only the
shared root event ledger, the shared $\RealUp$ endpoint-classifier rows, and
their named face rows. The public face supplies no mixed consumer row and no
analytic completion interface.
\end{theorem}
\begin{proof}
Begin with the outgoing rows in
\autoref{def:measure-root-public-face-exactness}. They are exactly the three
faces accepted by \autoref{def:measure-root-consumer-acceptance-gate}.

Apply \autoref{thm:measure-root-consumer-acceptance-separation}. It identifies
the only overlaps among the integral, probability, and functional-analysis
faces as the shared $\mathsf{BHist}$ event ledger and the shared $\RealUp$
endpoint classifier rows.

Next apply \autoref{thm:measure-root-probspace-integral-consumer-surface} and
\autoref{thm:measure-root-real-stream-consumer-regularity-boundary}. These
theorems read the same consumers through displayed event rows, StreamName
observations, endpoint comparisons, finite readbacks, normalization rows,
monotone rows, and relative-difference rows.

Finally use \autoref{thm:measure-root-source-deps-ready-package}. The source
package is built before any outgoing consumer face is read, so consumer rows
cannot become source hypotheses and cannot merge the named faces. Hence the
public endpoint fiber separates $\IntegralUp$, $\ProbSpaceUp$, and
$\FunctionalAnalysisUp$ exactly as stated, with no host set equality,
quotient event equality, analytic completion object, or standard bridge row.
\end{proof}
