\begin{definition}[Measure StreamName endpoint family]
\label{def:measure-streamname-endpoint-family}
A $\MeasureUp$ StreamName endpoint family over the sigma-algebra carrier
surface of \autoref{def:measure-sigma-algebra-carrier-surface} is a
certified observation map $s:\Hist\to\Hist$ together with a displayed
$\mathsf{RatStreamNameCarrier}(s)$ row as in
\autoref{def:rat-stream-name-carrier}. For every unary observation history
$n$ with $\mathsf{UnaryHistory}(n)$, the point observation $s(n)$ carries:
\begin{enumerate}
  \item a $\MeasureUp$ measurable-event row covered by
  \autoref{def:measure-event-row-coverage};
  \item the associated $\RealUp$ endpoint row $\mu(s(n))$ read through the
  endpoint classifier of \autoref{def:real-classifier-specification};
  \item the pointwise StreamNameUp classifier row supplied by
  \autoref{def:rat-stream-name-classifier};
  \item the countable-sum endpoint row attached to the resulting
  StreamName-indexed measurable family.
\end{enumerate}
The family exposes no host-level equality of event carriers. Its public data
are exactly the unary $\mathsf{BHist}$ observation, the covered measurable
event, its $\hsame$ transport row, and the corresponding $\RealUp$ endpoint
classifier row.
\end{definition}

\begin{theorem}[Measure StreamName endpoint carrier-classifier]
\label{thm:measure-streamname-endpoint-carrier-classifier}
Every $\MeasureUp$ StreamName endpoint family supplies carrier transport for
the StreamName observation map and pointwise classifier transport for its
measurable-event and $\RealUp$ endpoint rows. The transport is the common
projection of \autoref{def:rat-stream-name-carrier},
\autoref{def:rat-stream-name-classifier},
\autoref{thm:rat-stream-name-certificate-fields}, and
\autoref{thm:measure-carrier-classifier-obligation}.
\end{theorem}
\begin{proof}
Project the $\mathsf{RatStreamNameCarrier}(s)$ row from
\autoref{def:measure-streamname-endpoint-family}. For a unary observation
$n$, \autoref{def:rat-stream-name-carrier} reads $s(n)$ as the carried point
history, and \autoref{def:rat-stream-name-classifier} identifies classifier
transport pointwise at the same unary observation.

Apply \autoref{thm:rat-stream-name-certificate-fields}. Its endpoint-carrier
and transported-classifier fields move the stream carrier and the pointwise
classifier row to the transported observation map.

Now apply \autoref{thm:measure-carrier-classifier-obligation} at that point
observation. The covered measurable-event row, the event ledger entry, and the
$\RealUp$ endpoint comparison are all componentwise rows of the
$\MeasureUp$ carrier surface, so they move along the same $\hsame$
classifier.

Repack the transported stream carrier, the transported covered event, and the
transported endpoint comparison into the endpoint family surface of
\autoref{def:measure-streamname-endpoint-family}. No quotient event equality
or host carrier equality is introduced.
\end{proof}

\begin{theorem}[Measure StreamName endpoint stability]
\label{thm:measure-streamname-endpoint-stability}
Let $s,t:\Hist\to\Hist$ be two $\MeasureUp$ StreamName endpoint families. If
$\mathsf{RatStreamNameClassifier}(s,t)$ holds and the endpoint family rows are
transported pointwise by $\hsame$ at every unary observation, then measurable
event witnesses and $\RealUp$ endpoint comparisons are preserved at every
index.
\end{theorem}
\begin{proof}
Fix a unary observation $n$ with witness
$\nu:\mathsf{UnaryHistory}(n)$. The StreamName classifier gives the point
classifier between $s(n)$ and $t(n)$ by
\autoref{def:rat-stream-name-classifier}.

The endpoint-family hypotheses attach a covered measurable-event row and a
$\RealUp$ endpoint row to the source point observation. The pointwise
$\hsame$ transport row moves the displayed event witness to the target point.

Apply \autoref{thm:measure-carrier-classifier-obligation} to the moved point
row. It transports the measurable-event witness and reads the measure value in
the target presentation under the same $\RealUp$ endpoint classifier.

Since the observation $n$ was arbitrary, the transported event witnesses and
endpoint comparisons assemble pointwise over all unary observations. Repacking
them gives stability of the whole StreamName endpoint family.
\end{proof}

\begin{theorem}[Measure StreamName countable-additivity scope]
\label{thm:measure-streamname-countable-additivity-scope}
For a $\MeasureUp$ StreamName endpoint family, the countable-additivity row of
\autoref{def:measureup-countable-additivity-row} factors only through the
StreamName-indexed endpoint family, the countable-sum classifier stability of
\autoref{thm:measure-obligation-countable-sum-classifier-stability}, and the
sigma-additivity obligation of \autoref{thm:measure-sigma-additivity-obligation}.
\end{theorem}
\begin{proof}
Read the StreamName endpoint family pointwise. Each unary observation supplies
a covered measurable-event row and its $\RealUp$ endpoint row, so the
StreamName map gives the measurable sequence consumed by the
countable-additivity row.

Apply \autoref{thm:measure-sigma-additivity-obligation} to that displayed
sequence, its pairwise-disjointness witness, and its countable-union row. The
resulting comparison is exactly the $\RealUp$ classifier relation between the
measure of the union and the countable endpoint sum.

If the point endpoints are transported along another StreamName classifier,
apply
\autoref{thm:measure-obligation-countable-sum-classifier-stability}. It turns
the pointwise $\RealUp$ endpoint comparisons into the classifier comparison
between the two countable sums.

Thus countable additivity reads no row beyond the StreamName endpoint family,
the countable-sum stability row, and the displayed sigma-additivity row of
$\MeasureUp$.
\end{proof}

\begin{theorem}[Measure StreamName downstream consumer boundary]
\label{thm:measure-streamname-downstream-consumer-boundary}
The $\IntegralUp$, $\ProbSpaceUp$, and $\FunctionalAnalysisUp$ consumers of
\autoref{def:measure-root-consumer-package} read only the StreamName-indexed
endpoint rows of \autoref{def:measure-streamname-endpoint-family} together
with the root consumer rows already listed in
\autoref{def:measure-root-consumer-package}.
\end{theorem}
\begin{proof}
Project the root consumer package of
\autoref{def:measure-root-consumer-package}. Its visible rows are the covered
measurable-event rows, the $\RealUp$ endpoint classifier rows, the
countable-sum endpoint rows, the finite readback rows, the relative-difference
and order rows, and the no-$\StdBridge$ boundary.

For $\IntegralUp$, the StreamName endpoint family supplies the covered
measurable sequence and countable endpoint rows already named by the root
consumer package. The finite and head-tail rows are then read from the same
package, not from an additional event equality surface.

For $\ProbSpaceUp$, the total-event and empty-zero rows are projections of the
root package. A StreamName endpoint family may index the measurable rows it
uses, but the probability consumer still receives only the normalization,
empty-zero, and finite-additivity rows listed there.

For $\FunctionalAnalysisUp$, the nonnegative, monotone,
relative-difference, and countable-sum classifier rows are exactly the
endpoint rows transported pointwise by
\autoref{thm:measure-streamname-endpoint-stability}. Repacking the three
consumer projections gives the stated boundary and adds no quotient event
equality, host set equality, or standard bridge row.
\end{proof}
