\begin{theorem}[RegularCauchyTailMeet limit-seal threshold route]
\label{thm:regular-cauchy-tail-meet-limit-seal-threshold-route}
Let $T=(R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N)$ be an accepted $\RegularCauchyTailMeetUp$ packet. Any $\CauchyLimitSealUp$ consumer or diagonal $\RealUp$ consumer that reads the public shared threshold of $T$ factors through the paired $\RegularCauchyNameUp$ source rows, paired $\StreamNameUp$ schedules, source modulus rows, shared $\DyadicRatCoreUp$ threshold ledger, paired comparison row, visible $\BHist$ evidence, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The route consumed by \autoref{ch:concrete-instances-cauchylimitseal-namecert} and by diagonal $\RealUp$ readers is therefore the same finite TailMeet certificate route, not a selected limit, quotient stream, host real equality, hidden tail oracle, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_limit\_seal\_threshold\_route}
\begin{proof}
First read the accepted carrier through the obligation package. It exposes the paired source rows, scheduled windows, source modulus rows, shared threshold ledger, paired comparison row, componentwise transports, continuations, finite ledger, provenance, and local name as one finite TailMeet surface.

Next compose shared-threshold cofinality with the dyadic endpoint meet. Cofinal refinement keeps stronger precision requests on the displayed source modulus rows, while the endpoint meet supplies the threshold ledger row consumed by the real-facing route.

Use the real-seal handoff, the diagonal-window threshold handoff, and the public shared-threshold certificate. These results make the $\CauchyLimitSealUp$ and diagonal $\RealUp$ consumers read the threshold only after the same finite route has been displayed.

The exclusion boundary is inherited from consumer exactness. Since the consumer receives only the listed TailMeet rows, there is no coordinate from which to export a quotient stream, selected limit, host real equality, hidden tail oracle, or ambient completeness witness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet observation-budget absorption]
\label{thm:regular-cauchy-tail-meet-observation-budget-absorption}
Every $\RealObservationBudgetUp$ request that reads the public shared threshold of an accepted $\RegularCauchyTailMeetUp$ packet is absorbed by the same finite TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The observation route of \autoref{ch:concrete-instances-real-observation-budget-namecert} may inspect its own finite request, window, dyadic readback, regular-rational handoff, and seal rows only through that displayed TailMeet entrance. It cannot add a hidden observation budget, host real equality, selected limit, or ambient completeness row to the threshold read.
\end{theorem}
\begin{proof}
Begin with the public shared-threshold certificate. It names $\tau$ as the threshold exported to real-facing consumers and keeps the export attached to the paired regular-Cauchy sources, stream schedules, source modulus rows, comparison row, transports, continuations, ledger, provenance, and local name.

Now route the request through the finite observation-budget surface. That sibling chapter admits observation reads through finite request rows, windows, dyadic readbacks, regular-rational handoff rows, and a real-seal boundary, so the TailMeet threshold can enter it only through the displayed finite entrance.

Finally apply the real-seal handoff and consumer exactness. The handoff places the budget read behind the same TailMeet threshold route, and exactness prevents the budget side from appending a host equality row, selected limit, hidden observation budget, or ambient completeness premise.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet selector-budget public route]
\label{thm:regular-cauchy-tail-meet-selector-budget-public-route}
Every $\RegularCauchySelectorBudgetUp$ route that shares the public threshold of an accepted $\RegularCauchyTailMeetUp$ packet reuses the displayed selector-window and $\RegSeqRatUp$ route of \autoref{ch:concrete-instances-regularcauchyselectorbudget-namecert}. Its tail-facing threshold entry is the TailMeet row $\tau$ transported through
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N,
$$
and it creates no second selector, hidden threshold, hidden tail oracle, quotient stream, host real equality, selected limit, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_selector\_budget\_public\_route}
\begin{proof}
Start with selector admission and the selector-budget surface. The admitted route supplies the finite selector windows and $\RegSeqRatUp$ readback before any tail-facing threshold is consumed.

Next use the shared-threshold cofinality and route determinacy rows. Cofinality allows stronger displayed thresholds only through $M_0$ and $M_1$, and determinacy keeps any shared-threshold read with the same transported source, window, and modulus rows on the same $\tau$.

Attach the public shared-threshold certificate and the diagonal-window threshold handoff. They present the selector-facing threshold as the same public TailMeet row consumed by real-facing routes, with $Q,H,C,L,N$ carried along the displayed package and naming surface.

Thus the selector-budget consumer reuses the existing selector-window and $\RegSeqRatUp$ route. With no second threshold coordinate and no extra selector row in the TailMeet carrier, a hidden tail oracle or ambient completion datum cannot be introduced.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet triple consumer route factorization]
\label{thm:regular-cauchy-tail-meet-consumer-route-triple-factorization}
Any accepted consumer among $\CauchyLimitSealUp$, $\RealObservationBudgetUp$, and $\RegularCauchySelectorBudgetUp$ that reads a $\RegularCauchyTailMeetUp$ shared threshold factors through the same finite rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N .
$$
No such consumer may append selected limits, quotient stream equality, host real equality, hidden observation budgets, hidden tail oracles, or ambient completeness rows to that threshold read.
\end{theorem}
\begin{proof}
First use the limit-seal threshold route. It sends every $\CauchyLimitSealUp$ and diagonal $\RealUp$ threshold read through the paired regular-Cauchy sources, stream schedules, modulus rows, threshold ledger, comparison row, transports, continuations, package, and naming rows.

Next use observation-budget absorption. A $\RealObservationBudgetUp$ request may inspect its own finite budget surface only after the same TailMeet entrance has been displayed, so it receives $\tau$ with the rows $R_0,R_1,W_0,W_1,M_0,M_1,Q,H,C,L,N$ attached.

Finally use the selector-budget public route. The selector-facing threshold is the same public TailMeet row, transported through the same finite packet and not through a second selector or hidden threshold coordinate.

The three routes therefore share the displayed row list. Since each preceding theorem excludes selected limits, quotient stream equality, host real equality, hidden observation budgets, hidden tail oracles, and ambient completeness rows, their common factorization excludes the same extra coordinates.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet Real and completion consumer frontier]
\label{thm:regular-cauchy-tail-meet-real-completion-consumer-frontier}
Let $T=(R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N)$ be an accepted $\RegularCauchyTailMeetUp$ packet. Any $\RealUp$ or $\CompletionUp$ consumer that reads the shared threshold of $T$ through $\CauchyLimitSealUp$, $\RealObservationBudgetUp$, or $\RegularCauchySelectorBudgetUp$ must first factor through the single finite TailMeet packet
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
No such consumer may bypass that frontier by using selected limits, quotient stream equality, host real equality, trichotomy rows, hidden observation budgets, hidden tail oracles, or ambient completeness.
\end{theorem}
\begin{proof}
Use the limit-seal threshold route to place every $\CauchyLimitSealUp$ and diagonal $\RealUp$ read behind the paired source rows, stream schedules, modulus rows, shared threshold ledger, comparison row, transports, continuations, package provenance, and local name.

Next use observation-budget absorption and the selector-budget public route. These results show that the observation and selector surfaces can consume $\tau$ only through the same displayed rows; their own budget, selector, window, and readback coordinates do not create another entrance to the threshold.

Apply the triple consumer route factorization. It already identifies the common route for the three downstream consumer surfaces, so a $\RealUp$ or $\CompletionUp$ consumer meeting any of them receives the same finite TailMeet packet before any seal-facing or completion-facing read.

The refused objects are not coordinates of that packet. Selected limits, quotient stream equality, host real equality, trichotomy rows, hidden observation budgets, hidden tail oracles, and ambient completeness therefore cannot be exported through the common frontier.
\end{proof}
