\begin{theorem}[RegularCauchyTailMeet observation-budget factorization]
\label{thm:regular-cauchy-tail-meet-observation-budget-factorization}
Any $\RealObservationBudgetUp$ consumer that reads an accepted $\RegularCauchyTailMeetUp$ threshold must first factor its observation request through the TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
before it reaches the observation-budget rows. Thus the budget consumer sees the paired $\RegularCauchyNameUp$ sources, paired $\StreamNameUp$ windows, source modulus rows, shared threshold, comparison row, componentwise transports, displayed continuations, finite ledger, provenance, and local $\NameCert$ row as the complete entrance to the finite observation-budget surface of \autoref{ch:concrete-instances-real-observation-budget-namecert}.
\end{theorem}
\begin{proof}
Start with the finite observation-budget route of \autoref{ch:concrete-instances-real-observation-budget-namecert}. A budget consumer can inspect only the precision request, finite window family, dyadic readbacks, regular-sequence handoff, real-seal boundary, transports, continuations, provenance, and local naming rows supplied by its accepted packet.

Next read the TailMeet threshold through shared-threshold non-escape. By \autoref{thm:regular-cauchy-tail-meet-shared-threshold-nonescape}, every admitted shared-threshold read remains inside the displayed threshold, paired stream schedules, source modulus rows, comparison row, componentwise transports, continuation routes, provenance, and local $\NameCert$ evidence.

Finally apply real-seal route totality. \autoref{thm:regular-cauchy-tail-meet-real-seal-route-totality} places every admitted $\RealUp$ seal read behind the same TailMeet window and dyadic endpoint rows, so the observation-budget consumer cannot reach its budget rows before the TailMeet route has exposed $R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N$.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet selector-budget compatibility]
\label{thm:regular-cauchy-tail-meet-selector-budget-compatibility}
Any $\RegularCauchySelectorBudgetUp$ route that shares the accepted $\RegularCauchyTailMeetUp$ threshold consumes that threshold through the selector budget's finite-window and $\RegSeqRatUp$ route. It does not introduce a second selector, a hidden threshold, or an independent tail oracle outside the displayed rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
\end{theorem}
\begin{proof}
Read the selector-budget side through \autoref{ch:concrete-instances-regularcauchyselectorbudget-namecert}. Its finite-window and $\RegSeqRatUp$ rows specify the admissible selector request before any downstream tail read is exported.

Now compose with shared-threshold route determinacy. By \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}, two shared-threshold reads with the same transported source rows, window rows, and source modulus rows reach the same displayed dyadic threshold ledger.

The selector-budget route therefore consumes the TailMeet threshold through the already displayed finite-window and regular-rational route. Since determinacy leaves no second threshold coordinate and the selector budget supplies no extra selector outside its finite route, the shared threshold cannot be replaced by a hidden threshold or independent tail oracle.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet real-tail agreement consumer surface]
\label{thm:regular-cauchy-tail-meet-real-tail-agreement-consumer-surface}
Every $\RealTailAgreementSealUp$ consumer of an accepted $\RegularCauchyTailMeetUp$ packet receives exactly the shared threshold $\tau$, paired comparison row $Q$, componentwise transports $H$, displayed continuations $C$, package provenance, finite ledger $L$, and local $\NameCert$ row $N$, together with the paired source, window, and modulus rows that produce $\tau$.

The consumer surface is therefore the finite TailMeet route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N,
$$
followed by the seal route of \autoref{ch:concrete-instances-realtailagreementseal-namecert}. It includes no quotient stream, selected limit, host equality, independent tail oracle, or ambient completeness row.
\end{theorem}
\begin{proof}
First use the observation-budget factorization. \autoref{thm:regular-cauchy-tail-meet-observation-budget-factorization} forces every real-facing observation of the TailMeet threshold through the displayed source, window, modulus, threshold, comparison, transport, continuation, ledger, provenance, and local naming rows before any budget-side read is available.

Next use selector-budget compatibility. \autoref{thm:regular-cauchy-tail-meet-selector-budget-compatibility} keeps selector-facing reads on the same finite-window and $\RegSeqRatUp$ route to the shared threshold, so the real-tail agreement consumer receives the same $\tau$ and $Q$ rather than a second selector or hidden tail threshold.

Finally read the seal side through \autoref{ch:concrete-instances-realtailagreementseal-namecert}. The agreement seal may consume the shared threshold, paired comparison, transports, continuations, provenance, ledger, and local naming evidence already displayed by the TailMeet packet, but the TailMeet carrier and the two preceding consumer theorems provide no coordinate for quotient streams, selected limits, host equality, independent tail oracles, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet budget-family cofinality]
\label{thm:regular-cauchy-tail-meet-budget-family-cofinality}
For any finite family of downstream budget requests accepted through a $\RegularCauchyTailMeetUp$ packet, the shared threshold row remains cofinal. Every requested strengthening factors through the same finite route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
and a stronger displayed dyadic threshold can be chosen inside that route for all members of the family at once. No request introduces a quotient stream, selected limit, host equality, independent tail oracle, trichotomy row, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with window-source coverage and source-modulus exhaustion. \autoref{thm:regular-cauchy-tail-meet-window-source-coverage} and \autoref{thm:regular-cauchy-tail-meet-source-modulus-exhaustion} force each family request through the two source rows, two window rows, and two source modulus rows before it reaches $\tau$.

Use shared-threshold cofinality for the finite family. Since \autoref{thm:regular-cauchy-tail-meet-shared-threshold-cofinality} refines the displayed threshold without leaving the carrier route, induction over the finite family yields one stronger displayed threshold row still carried by the same ledger.

Finally apply ledger exactness and the public shared-threshold certificate. \autoref{thm:regular-cauchy-tail-meet-ledger-exactness} and \autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate} keep the refined family threshold inside the finite certificate surface, so none of the excluded completion or quotient data can be exported.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet finite witness induction]
\label{thm:regular-cauchy-tail-meet-finite-witness-induction}
Let a finite list of downstream requests enter through an accepted $\RegularCauchyTailMeetUp$ packet, with each entry either a $\RealObservationBudgetUp$ request or a $\RegularCauchySelectorBudgetUp$ request admitted by the packet. Then the whole list admits one displayed dyadic threshold row inside the same TailMeet route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The witness is obtained without adding a quotient stream, selected limit, host equality row, independent tail oracle, trichotomy coordinate, or ambient completeness premise.
\end{theorem}
\begin{proof}
For the empty list, use the displayed accepted packet itself. Its public shared-threshold certificate already carries $\tau$ together with $R_0,R_1,W_0,W_1,M_0,M_1,Q,H,C,L,N$, so the required witness is the original finite row.

For a nonempty list, assume by induction that the tail of the list has one displayed threshold row inside the same TailMeet route. The head request is either an observation-budget request or a selector-budget request.

In the observation-budget case, apply \autoref{thm:regular-cauchy-tail-meet-observation-budget-factorization}; in the selector-budget case, apply \autoref{thm:regular-cauchy-tail-meet-selector-budget-shared-entry}. In both cases the head request reaches the shared threshold only through the displayed source, window, modulus, comparison, transport, continuation, package, ledger, and local naming rows.

Now use \autoref{thm:regular-cauchy-tail-meet-budget-family-cofinality} to refine the induction witness and the head request to one stronger displayed threshold. Source-window-modulus route determinacy, \autoref{thm:regular-cauchy-tail-meet-source-window-modulus-route} and \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}, keeps that refined row on the same TailMeet route rather than on a second threshold coordinate.

Finally apply ledger exactness and the public shared-threshold certificate. \autoref{thm:regular-cauchy-tail-meet-ledger-exactness} and \autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate} exhaust the finite ledger surface for the refined witness, so the induction step has no coordinate from which to export quotient, selected-limit, host-equality, independent-tail, trichotomy, or completeness data.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet selector-budget absorption]
\label{thm:regular-cauchy-tail-meet-selector-budget-absorption}
Every $\RegularCauchySelectorBudgetUp$ request that enters through an accepted $\RegularCauchyTailMeetUp$ packet is absorbed by the displayed rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The selector-budget side may choose finite windows and regular-rational readbacks, but the tail-meet threshold it consumes is still the shared threshold row produced by the paired source schedules, source modulus rows, ledger exactness, public certificate, and seal-compatible handoff.
\end{theorem}
\begin{proof}
Read the selector-budget request through selector admission and selector-budget compatibility. \autoref{thm:regular-cauchy-tail-meet-selector-admission} supplies the admitted selector route, and \autoref{thm:regular-cauchy-tail-meet-selector-budget-compatibility} keeps that route on the selector budget's finite-window and $\RegSeqRatUp$ surface.

Next identify the threshold route. Window-source coverage, source-modulus exhaustion, and shared-threshold route determinacy force the selector-budget read through $R_0,R_1,W_0,W_1,M_0,M_1,\tau$ rather than through a second selector or hidden threshold.

The structural rows are then absorbed by consumer exactness and seal compatibility. \autoref{thm:regular-cauchy-tail-meet-consumer-exactness} and \autoref{thm:regular-cauchy-tail-meet-seal-compatibility} add exactly $Q,H,C,L,N$ to the route and exclude quotient streams, selected limits, host equality, independent tail oracles, trichotomy, and ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet diagonal seal-budget exactness]
\label{thm:regular-cauchy-tail-meet-diagonal-seal-budget-exactness}
Every diagonal $\RealUp$ seal-budget read of an accepted $\RegularCauchyTailMeetUp$ packet passes through the same finite shared-threshold route used by the public certificate:
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The diagonal seal may read the real-facing handoff only after the paired source schedules, source modulus rows, cofinal shared threshold, exact ledger, public shared-threshold certificate, and seal compatibility rows have all been exposed.
\end{theorem}
\begin{proof}
Begin with the diagonal-facing coverage. \autoref{thm:regular-cauchy-tail-meet-diagonal-window-threshold-handoff} and \autoref{thm:regular-cauchy-tail-meet-window-source-exhaustion} route the diagonal read through the displayed source schedules and window rows.

Attach the modulus and threshold rows. Source-modulus exhaustion, shared-threshold cofinality, and source-window-modulus route results identify the only admissible path to $\tau$ and keep stronger diagonal precision requests cofinal inside the same finite ledger.

Now read the seal side. \autoref{thm:regular-cauchy-tail-meet-ledger-exactness}, \autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate}, and \autoref{thm:regular-cauchy-tail-meet-seal-compatibility} make the diagonal seal consume exactly the listed threshold, comparison, transport, continuation, ledger, provenance, and naming rows, with no additional completion premise.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet selector-budget shared entry]
\label{thm:regular-cauchy-tail-meet-selector-budget-shared-entry}
Every $\RegularCauchySelectorBudgetUp$ consumer that enters through an accepted $\RegularCauchyTailMeetUp$ packet reads the same shared threshold row $\tau$ through
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The selector-budget request may choose its finite selector windows and $\RegSeqRatUp$ readback, but its tail-facing threshold entry is the TailMeet shared threshold ledger row, transported with the displayed comparison, $\hsame$ rows, continuations, package provenance, and local $\NameCert$ evidence.
\end{theorem}
\begin{proof}
Start from selector-budget compatibility. \autoref{thm:regular-cauchy-tail-meet-selector-budget-compatibility} routes the admitted selector request through the finite-window and $\RegSeqRatUp$ surface before any tail threshold is consumed.

Next use selector-budget absorption. \autoref{thm:regular-cauchy-tail-meet-selector-budget-absorption} identifies the absorbed TailMeet route as the displayed source schedules, source modulus rows, shared threshold, comparison row, transports, continuations, ledger, provenance, and local name.

Finally apply shared-threshold route determinacy. \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy} rules out a second threshold coordinate for the same transported source-window-modulus route, so the selector-budget consumer and the TailMeet packet read the same $\tau$.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet budget-family row exhaustion]
\label{thm:regular-cauchy-tail-meet-budget-family-row-exhaustion}
Let a finite family of downstream observation requests or $\RegularCauchySelectorBudgetUp$ requests enter through an accepted $\RegularCauchyTailMeetUp$ packet. Then every family member factors through the TailMeet carrier and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface. No member contributes a row outside
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
In particular, the family cannot add a quotient stream, selected limit, host equality row, independent tail oracle, trichotomy coordinate, or ambient completeness witness.
\end{theorem}
\begin{proof}
First use budget-family cofinality. \autoref{thm:regular-cauchy-tail-meet-budget-family-cofinality} gives one stronger displayed threshold inside the same TailMeet route for all finite family members.

Observation requests factor through \autoref{thm:regular-cauchy-tail-meet-observation-budget-factorization}. Selector-budget requests factor through \autoref{thm:regular-cauchy-tail-meet-selector-budget-shared-entry}. Both routes therefore meet at the same shared threshold row and retain the same comparison, transport, continuation, package, and naming rows.

It remains to exclude extra family rows. \autoref{thm:regular-cauchy-tail-meet-ledger-exactness} exhausts the finite ledger surface, so the family has no coordinate from which to export quotient, selected-limit, host-equality, independent-tail, trichotomy, or completeness data.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet real-tail threshold ledger]
\label{thm:regular-cauchy-tail-meet-real-tail-threshold-ledger}
Every $\RealTailAgreementSealUp$ read of an accepted $\RegularCauchyTailMeetUp$ packet consumes exactly the TailMeet shared threshold ledger before the real-tail seal route is available. The consumed rows are
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N,
$$
with $\tau$ supplied by the public shared-threshold certificate and transported through the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.
\end{theorem}
\begin{proof}
Begin with the real-tail agreement consumer surface. \autoref{thm:regular-cauchy-tail-meet-real-tail-agreement-consumer-surface} lists exactly the TailMeet rows visible to the $\RealTailAgreementSealUp$ side and gives no separate threshold oracle.

Next apply diagonal seal-budget exactness. \autoref{thm:regular-cauchy-tail-meet-diagonal-seal-budget-exactness} forces a real-facing seal-budget read through the displayed source schedules, source modulus rows, shared threshold, comparison, transports, continuations, ledger, provenance, and local name before the seal route is read.

Finally use the public shared-threshold certificate. \autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate} identifies the real-tail threshold with the same public $\tau$, so the agreement seal consumes exactly the TailMeet ledger and cannot introduce an additional real-tail threshold row.
\end{proof}
