\begin{theorem}[RegularCauchyTailMeet root downstream budget-seal package]
\label{thm:regular-cauchy-tail-meet-root-downstream-budget-seal-package}
For an accepted $\RegularCauchyTailMeetUp$ packet, every root threshold route exported to $\RealObservationBudgetUp$, $\ObservationBudgetLimiterUp$, $\CauchyModulusRefinementUp$, or $\CauchyLimitSealUp$ reaches a $\RealUp$ or $\CompletionUp$ seal read only after the route has passed through the displayed TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The route then passes through the finite observation-budget surface of \autoref{ch:concrete-instances-real-observation-budget-namecert} and the limiter cap surface of \autoref{ch:concrete-instances-observationbudgetlimiter-namecert}. Only after those rows are displayed may refinement or limit-seal consumers read the Real or completion seal surfaces of \autoref{ch:concrete-instances-cauchy-modulus-refinement-namecert} and \autoref{ch:concrete-instances-cauchylimitseal-namecert}. The package exports no quotient stream, selected limit, host real equality, trichotomy row, hidden selector, uncapped observation schedule, independent completion carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with the root budget-limiter factorization. By \autoref{thm:regular-cauchy-tail-meet-root-budget-limiter-factorization}, any route to $\RealObservationBudgetUp$, $\ObservationBudgetLimiterUp$, $\CauchyModulusRefinementUp$, or $\CauchyLimitSealUp$ first reads the TailMeet source, window, modulus, threshold, comparison, transport, continuation, ledger, and local naming rows.

Next use the budgeted refinement seal factorization. \autoref{thm:regular-cauchy-tail-meet-budgeted-refinement-seal-factorization} places the finite observation-budget entrance and the capped limiter service before the refinement and limit-seal consumers can reach a Real or completion seal.

The sibling chapter surfaces supply the downstream boundary. The observation-budget and limiter chapters expose only finite budget, window, readback, cap, service, transport, continuation, provenance, and local $\NameCert$ rows, while the refinement and limit-seal chapters read their Real and completion-facing seals through those finite rows.

Finally apply the root window threshold obligations from \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry}, \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization}, and \autoref{thm:regular-cauchy-tail-meet-observation-budget-limiter-cap-synchronization}. These keep every consumer on the displayed route and leave no carrier coordinate for quotient streams, selected limits, host real equality, trichotomy, hidden selectors, uncapped schedules, independent completion carriers, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root seal exactness]
\label{thm:regular-cauchy-tail-meet-root-seal-exactness}
For an accepted $\RegularCauchyTailMeetUp$ packet, any $\RealUp$ or $\CompletionUp$ seal read exported from a root threshold route to a $\CauchyModulusRefinementUp$ or $\CauchyLimitSealUp$ consumer is exact with respect to the displayed route: it must use the same TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
that appear in the root downstream budget-seal package, then the finite observation-budget surface, then the limiter cap surface, before the consumer may read the refinement or limit-seal interface. No downstream consumer may replace those rows by an independent threshold, budget, cap, Real carrier, completion carrier, quotient stream, selected limit, hidden selector, or ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with the package statement \autoref{thm:regular-cauchy-tail-meet-root-downstream-budget-seal-package}. It already places every exported route to $\RealObservationBudgetUp$, $\ObservationBudgetLimiterUp$, $\CauchyModulusRefinementUp$, or $\CauchyLimitSealUp$ on the displayed TailMeet rows before any $\RealUp$ or $\CompletionUp$ seal read is available.

Next fix the route through the budget and limiter interfaces. The root budget-limiter factorization \autoref{thm:regular-cauchy-tail-meet-root-budget-limiter-factorization} keeps the root threshold route on the TailMeet packet and then passes it through the limiter service, while \autoref{thm:regular-cauchy-tail-meet-budgeted-refinement-seal-factorization} places the refinement and limit-seal consumers after that finite budgeted route.

It remains to identify the rows read by the downstream seal. The observation-budget entry theorem \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry} supplies the finite budget entrance from the same root rows, and \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization} synchronizes the $\RealUp$ and $\CompletionUp$ seal reads with that entrance.

Finally \autoref{thm:regular-cauchy-tail-meet-observation-budget-limiter-cap-synchronization} synchronizes the limiter cap with the same route. Hence every downstream seal consumer reads exactly the displayed TailMeet rows, followed by the finite observation-budget and limiter cap surfaces, and there is no remaining coordinate from which an independent analytic or completion-side seal can be obtained.
\end{proof}
