\begin{theorem}[RegularCauchyTailMeet root consumer package]
\label{thm:regular-cauchy-tail-meet-root-consumer-package}
The selector admission theorem, seal compatibility theorem, public shared-threshold certificate, and bridge package assemble the downstream root package for $\RegularCauchyTailSelectorUp$, $\CauchyLimitSealUp$, $\RealDiagonalWindowCoverageUp$, and diagonal $\RealUp$ consumers.

The package exports one shared threshold route from the paired $\RegularCauchyNameUp$ sources and paired $\StreamNameUp$ schedules through source modulus rows, the dyadic threshold ledger, comparison row, componentwise $\hsame$ transports, displayed $\Cont$ continuations, finite ledger, $\Pkg$ provenance, and local $\NameCert$ rows. It exports no quotient stream, selected limit, host real equality, independent tail oracle, or ambient completeness principle.
\end{theorem}
\begin{proof}
First collect selector admission. It shows that every selector-facing precision and selected-tail read factors through one paired source schedule and the shared threshold row.

Next collect seal compatibility. It shows that $\CauchyLimitSealUp$ and diagonal $\RealUp$ consumers read the same threshold through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ route.

Add \autoref{thm:regular-cauchy-tail-meet-public-shared-threshold-certificate} and \autoref{thm:regular-cauchy-tail-meet-bridge-package}. The certificate serves $\RealDiagonalWindowCoverageUp$ and diagonal $\RealUp$ consumers, while the bridge package keeps completion-facing reads inside the same finite shared-tail packet.

The four consumer families therefore share one root package. Its rows are exactly the paired sources, schedules, modulus reads, threshold, comparison, transports, continuations, ledger, provenance, and local name already displayed by the carrier, so the excluded quotient, host, selection, oracle, and completeness data are not exported.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root carrier admission]
\label{thm:regular-cauchy-tail-meet-root-carrier-admission}
The root-facing admission surface for an accepted $\RegularCauchyTailMeetUp$ packet is the shared finite threshold row
$$
T=(R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N)
$$
of \autoref{def:regular-cauchy-tail-meet-carrier}. A downstream root consumer may admit the packet only after the paired $\RegularCauchyNameUp$ sources, paired $\StreamNameUp$ windows, paired source modulus rows, shared dyadic threshold, comparison row, componentwise $\hsame$ transports, displayed $\Cont$ routes, finite ledger, and local $\NameCert$ row are visible.
\end{theorem}
\begin{proof}
Start with the carrier and the local NameCert obligations. They display the two source rows, two scheduled windows, source modulus rows, threshold row, comparison row, transport rows, continuation rows, ledger, and local name.

Use window-source coverage. Every threshold-facing read must pass through the paired sources, paired windows, and paired source modulus rows before it reaches $\tau$.

Apply shared-threshold cofinality to the root-facing threshold. It keeps any strengthened threshold tied to the same paired schedules and source modulus rows, so root admission remains a finite shared-threshold row rather than an independent tail oracle.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root classifier stability]
\label{thm:regular-cauchy-tail-meet-root-classifier-stability}
For root-facing paired-window consumers, componentwise $\hsame$ transport of the rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
preserves the displayed comparison classifier. The transported root surface reads the same paired-window route to $\tau$ and $Q$, and it cannot replace the shared threshold by a quotient-stream, host-limit, selected-subsequence, or ambient-completeness classifier.
\end{theorem}
\begin{proof}
Project the paired-window route from the carrier. The classifier uses only the paired source rows, schedules, modulus rows, shared threshold, and comparison row.

Apply classifier stability and shared-threshold transport. The componentwise $\hsame$ rows move these coordinates together, and the displayed $\Cont$ routes replay the same window-to-threshold-to-comparison path.

Use paired-window ledger coverage to keep both scheduled windows recorded before a real-facing or root-facing read can consume the comparison. Since the ledger has no alternate classifier coordinate, the transported root surface preserves exactly the displayed comparison classifier.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root ledger exactness]
\label{thm:regular-cauchy-tail-meet-root-ledger-exactness}
The root-facing ledger of an accepted $\RegularCauchyTailMeetUp$ packet records exactly two input tails and one meet threshold: the rows $R_0,W_0,M_0$ for the first tail, the rows $R_1,W_1,M_1$ for the second tail, the shared dyadic threshold row $\tau$, the paired comparison row $Q$, and the structural rows $H,C,L,N$. No root-facing ledger entry records a third tail, an independent threshold, a quotient-stream equality, a selected limit, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with ledger exactness. It confines every accepted read to the route from the paired regular Cauchy sources through their windows and source modulus rows to $\tau$, $Q$, and the $\RealUp$ handoff.

Use paired-window ledger coverage. Both scheduled windows must be present in $L$ before the shared-tail certificate is available, so the ledger has exactly the two displayed input-tail sides.

Apply real-seal route totality. The real-facing route is already exhausted by the displayed shared threshold and comparison rows, so no additional tail or threshold can be introduced at the root boundary.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet uniform criterion consumer link]
\label{thm:regular-cauchy-tail-meet-uniform-criterion-consumer-link}
The root-facing $\RegularCauchyTailMeetUp$ obligation rows supply the shared-tail consumer link required by the $\UniformCauchyCriterionUp$ root surface of \autoref{thm:uniform-cauchy-criterion-root-shared-tail-meet}. A uniform-criterion consumer may read the meet packet only through the admitted shared threshold, the hsame-stable paired-window classifier, and the exact two-tail ledger of the preceding root rows.
\end{theorem}
\begin{proof}
First collect root carrier admission. It presents the shared finite threshold row required by a uniform Cauchy consumer.

Next collect root classifier stability. The paired-window comparison is preserved under componentwise $\hsame$ and displayed $\Cont$ replay, so the uniform criterion reads a stable shared-tail classifier.

Finally collect root ledger exactness and apply \autoref{thm:uniform-cauchy-criterion-root-shared-tail-meet}. The uniform criterion receives exactly the two input tails and one meet threshold already recorded by the $\RegularCauchyTailMeetUp$ ledger, with no quotient, host-limit, selection, oracle, or completeness data available outside that finite route.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet window-source exhaustion]
\label{thm:regular-cauchy-tail-meet-window-source-exhaustion}
Every accepted $\RegularCauchyTailMeetUp$ comparison reads exactly the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the shared-tail carrier. It has no additional window source beyond the paired regular Cauchy names, paired stream schedules, source modulus rows, dyadic threshold ledger, comparison row, componentwise transports, displayed continuations, package provenance, and local naming row.
\end{theorem}
\begin{proof}
Begin with the carrier and the window-source coverage theorem. They display the two regular Cauchy sources, the two stream schedules, the source modulus rows, the dyadic threshold ledger, and the comparison row.

Apply consumer exactness. It states that comparison-facing reads are confined to the displayed carrier rows and the componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.

Use the root consumer package to repack the route for downstream consumers. The resulting comparison therefore exhausts the listed source rows and exposes no extra window, oracle, quotient stream, host limit, or ambient completeness row.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet shared-threshold non-escape]
\label{thm:regular-cauchy-tail-meet-shared-threshold-nonescape}
Shared-threshold reads of an accepted $\RegularCauchyTailMeetUp$ packet cannot introduce a host limit, quotient stream equality, or choice-selected subsequence. Every such read remains inside the shared dyadic threshold, the paired stream schedules, the source modulus rows, the comparison row, the componentwise $\hsame$ transports, the displayed $\Cont$ routes, the $\Pkg$ provenance, and the local $\NameCert$ evidence.
\end{theorem}
\begin{proof}
Start with the shared-threshold transport theorem. It identifies threshold transport with the displayed schedule, modulus, dyadic, comparison, and transport rows.

Next use diagonal consumer non-escape. That theorem rules out quotient stream equality, host real equality, selected subsequences, hidden tail oracles, and ambient completeness data for diagonal consumers of the same packet.

The root package sends shared-threshold consumers through the same route. Hence a shared-threshold read can preserve the finite threshold evidence, but it cannot create any of the excluded host, quotient, or selection data.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet real-seal route totality]
\label{thm:regular-cauchy-tail-meet-real-seal-route-totality}
Any $\RealUp$ seal consumer of an accepted $\RegularCauchyTailMeetUp$ packet must pass through the same tail-meet window and dyadic endpoint rows before reading the real seal. The route is total for admitted seal reads because the real-seal handoff, dyadic endpoint meet, consumer exactness, diagonal non-escape, and root consumer package share the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ boundary.
\end{theorem}
\begin{proof}
First use the real-seal handoff. It places every $\RealUp$ seal read behind the shared threshold route, comparison row, transport rows, continuations, ledger, provenance, and local name.

Then use the dyadic endpoint meet. The endpoint data consumed by the seal route are the displayed $\DyadicRatCoreUp$ threshold and endpoint rows, not a host real limit or quotient stream witness.

Finally combine consumer exactness, diagonal non-escape, and the root consumer package. These theorems keep every admitted seal read inside the same finite tail-meet window, so the route is total for accepted consumers and exports no hidden completion principle.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet source-window-modulus route]
\label{thm:regular-cauchy-tail-meet-source-window-modulus-route}
Every shared-threshold read of an accepted $\RegularCauchyTailMeetUp$ packet factors through the paired $\RegularCauchyNameUp$ source rows, the paired $\StreamNameUp$ window rows, and the source modulus rows before it reaches the displayed dyadic threshold ledger. The route is a finite $\BHist$ route recorded by the carrier, the local $\NameCert$ obligations, ledger exactness, shared-threshold cofinality, and real-seal route totality.
\end{theorem}
\begin{proof}
Begin with the carrier and NameCert obligations. They expose the paired regular Cauchy source rows, stream windows, source modulus rows, dyadic threshold ledger, comparison row, transports, continuations, provenance, and local name as displayed coordinates.

Use shared-threshold cofinality and ledger exactness next. Any threshold read that refines the common tail must first choose the visible source rows, then the matching window rows, and then the modulus rows that justify the dyadic threshold coordinate.

Finally apply real-seal route totality. It routes admitted seal-facing reads through the same tail-meet window before any real-seal observation is read, so the source-window-modulus factorization is the common route for shared-threshold consumers.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet formal target envelope]
\label{thm:regular-cauchy-tail-meet-formal-target-envelope}
Every accepted $\RegularCauchyTailMeetUp$ packet whose source-window-modulus route is read by a $\FiniteObservationBudgetSelectorUp$ or $\CauchyLimitSealUp$ consumer factors through the same paired $\RegSeqRatUp$ sources, $\StreamNameUp$ windows, $\DyadicRatCoreUp$ threshold ledger, comparison row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and $\NameCert$ row before any $\RealUp$ seal is exposed. The downstream budget-selector and limit-seal reads therefore consume one finite handoff, not a hidden completion route and not a quotient-stream route.
\end{theorem}
\begin{proof}
Begin with root carrier admission, root classifier stability, and root ledger exactness. These rows identify the accepted packet as the displayed two-source, two-window, one-threshold surface and keep transported comparisons inside the same finite ledger.

Use real-seal route totality and the source-window-modulus route. They place every seal-facing read behind the paired sources, paired windows, source modulus rows, dyadic threshold, comparison, transports, continuations, provenance, and local name before the $\RealUp$ seal can be read.

Now read the consumer rows in the $\FiniteObservationBudgetSelectorUp$ and $\CauchyLimitSealUp$ surfaces. The selector consumes finite window and dyadic-budget rows before its seal handoff, while the limit seal consumes the same shared threshold route before exposing a completion-facing seal.

The two downstream routes therefore meet at the same finite handoff. Since neither consumer receives an additional quotient stream, host-limit equality, selected representative, or ambient completeness coordinate, the formal target envelope is exactly the displayed $\RegularCauchyTailMeetUp$ route.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet formal handoff Lean target]
\label{thm:regular-cauchy-tail-meet-formal-handoff-lean-target}
The root carrier admission, root classifier stability, root ledger exactness, source-window-modulus route, real-seal route totality, and formal target envelope jointly determine the exact finite handoff for a later Lean target over $\RegularCauchyTailMeetUp$. That handoff consists of paired $\RegSeqRatUp$ sources, paired $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ threshold row, the comparison row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$.

The target contains no quotient stream, host limit, selected subsequence, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with root carrier admission, root classifier stability, and root ledger exactness. These rows fix the two source rows, two window rows, threshold ledger, comparison row, transports, continuations, provenance, and local name as one finite carrier surface.

Next apply the source-window-modulus route. It identifies how the paired sources and windows reach the displayed dyadic threshold row before a shared-threshold read can proceed.

Use real-seal route totality and the formal target envelope for the downstream boundary. They require seal-facing consumers and formal consumers to read the same finite handoff before any $\RealUp$ seal is exposed.

Thus a later Lean target has an exact object to encode: the paired sources, paired windows, threshold, comparison, transports, routes, provenance, and local name. The excluded quotient, host-limit, subsequence, and completeness data have no coordinate in that object.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetFormalHandoffLeanTarget}

\begin{theorem}[RegularCauchyTailMeet window-budget exhaustion]
\label{thm:regular-cauchy-tail-meet-window-budget-exhaustion}
Every budget-selector or $\CauchyLimitSealUp$ consumer of an accepted $\RegularCauchyTailMeetUp$ packet exhausts its read through the two $\RegSeqRatUp$ source rows, two $\StreamNameUp$ windows, the two source modulus rows, the shared $\DyadicRatCoreUp$ threshold, comparison row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. The consumer receives no further budget window, hidden Cauchy tail, quotient stream equality, selected limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the source-window-modulus route, \autoref{thm:regular-cauchy-tail-meet-source-window-modulus-route}. It sends every shared-threshold read through the paired regular Cauchy source rows, paired stream windows, and source modulus rows before the dyadic threshold ledger can be read.

Next apply root ledger exactness and real-seal route totality, \autoref{thm:regular-cauchy-tail-meet-root-ledger-exactness} and \autoref{thm:regular-cauchy-tail-meet-real-seal-route-totality}. These keep the shared threshold, comparison row, transports, continuations, provenance, and local name on the same finite root surface for every admitted seal-facing read.

Finally use the formal target envelope and handoff target, \autoref{thm:regular-cauchy-tail-meet-formal-target-envelope} and \autoref{thm:regular-cauchy-tail-meet-formal-handoff-lean-target}. The budget-selector and $\CauchyLimitSealUp$ routes therefore consume exactly the displayed window-budget handoff, and the packet has no remaining coordinate for a second budget window, hidden tail, quotient stream equality, selected limit, or ambient completeness datum.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet shared-threshold route determinacy]
\label{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}
Two shared-threshold reads of an accepted $\RegularCauchyTailMeetUp$ packet that use the same transported $\RegularCauchyNameUp$ source rows, the same transported $\StreamNameUp$ window rows, and the same transported source modulus rows reach the same displayed dyadic threshold ledger. The determinacy is internal to the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.
\end{theorem}
\begin{proof}
Project both reads through the source-window-modulus route. By hypothesis the transported source rows, window rows, and source modulus rows agree componentwise under the displayed $\hsame$ transport.

Apply classifier stability and ledger exactness. The paired-window classifier cannot distinguish two reads with the same transported source, window, and modulus coordinates, and the exact ledger has only the displayed dyadic threshold coordinate for that route.

The $\Cont$, $\Pkg$, and $\NameCert$ rows then report the same finite ledger entry. Hence both reads reach the same displayed dyadic threshold ledger without invoking quotient stream equality, host limits, or choice-selected subsequences.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet public tail-meet certificate]
\label{thm:regular-cauchy-tail-meet-public-tail-meet-certificate}
The source-window-modulus route, shared-threshold route determinacy, and the public shared-threshold certificate assemble a public $\RegularCauchyTailMeetUp$ tail-meet certificate. Any public consumer receives the paired regular Cauchy sources, paired stream windows, source modulus rows, dyadic threshold ledger, comparison row, transports, continuations, provenance, and local NameCert evidence, and receives no quotient stream equality, selected limit, host real equality, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First use \autoref{thm:regular-cauchy-tail-meet-source-window-modulus-route}. It gives the public consumer a finite route from source rows through stream windows and source modulus rows to the displayed dyadic threshold ledger.

Next use \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}. It makes the displayed threshold ledger independent of duplicate reads that carry the same transported source, window, and modulus coordinates.

Finally combine the public shared-threshold certificate with real-seal route totality. The public certificate exposes the shared threshold as finite NameCert data, while the route-totality boundary keeps seal-facing consumers inside the same tail-meet window and excludes quotient, selection, host-equality, and ambient-completeness data.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root threshold source ledger]
\label{thm:regular-cauchy-tail-meet-root-threshold-source-ledger}
Every root-facing threshold read of an accepted $\RegularCauchyTailMeetUp$ packet factors through
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
before it reaches a downstream root consumer.
\end{theorem}
\begin{proof}
Project the carrier to expose the two source rows $R_0,R_1$, the two window rows $W_0,W_1$, the two modulus rows $M_0,M_1$, the shared threshold $\tau$, comparison row $Q$, transport $H$, continuation $C$, ledger $L$, and local name $N$.

Apply the root carrier admission, root classifier stability, and root ledger exactness results. They identify those displayed rows as the root-facing threshold surface and exclude a second root threshold coordinate.

Finally use the uniform-criterion consumer link. It reads the same finite ledger before any UniformCauchyCriterionUp consumer sees the packet, so every root-facing threshold read factors through the listed rows.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root shared-threshold coverage]
\label{thm:regular-cauchy-tail-meet-root-shared-threshold-coverage}
The shared threshold $\tau$ in an accepted $\RegularCauchyTailMeetUp$ packet covers both source modulus rows $M_0$ and $M_1$ before any $\RealUp$ or $\UniformCauchyCriterionUp$ consumer reads the packet.
\end{theorem}
\begin{proof}
Use the carrier and root carrier admission to project the paired sources, windows, modulus rows, and shared threshold.

Apply root classifier stability and root ledger exactness. The threshold row is recorded once in the ledger and is classified against both source modulus rows, so it is not a one-sided witness.

Then apply the uniform-criterion consumer link together with the real-seal route. Both downstream consumers enter through the same displayed threshold ledger, hence the shared threshold covers $M_0$ and $M_1$ before either consumer reads the packet.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root consumer exhaustion]
\label{thm:regular-cauchy-tail-meet-root-consumer-exhaustion}
Downstream consumers of an accepted $\RegularCauchyTailMeetUp$ packet receive only the two-tail, one-threshold finite ledger. They receive no quotient stream, selected limit, host equality, trichotomy, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with the carrier and the public tail-meet certificate. They expose exactly the paired source rows, paired window rows, source modulus rows, one shared threshold ledger, comparison, transport, continuations, package provenance, and local name.

Apply root ledger exactness and root classifier stability. These results keep root consumers on the displayed two-tail and one-threshold surface rather than on a quotient or selected-limit surface.

Finally use the uniform-criterion consumer link. It reuses the same finite ledger for downstream reads, so quotient stream, selected limit, host equality, trichotomy, and ambient completeness rows are unavailable to those consumers.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root threshold provenance]
\label{thm:regular-cauchy-tail-meet-root-threshold-provenance}
Every root threshold read of an accepted $\RegularCauchyTailMeetUp$ packet is sourced by the displayed rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
and inherits provenance only from the contributing $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project the carrier and use \autoref{thm:regular-cauchy-tail-meet-public-tail-meet-certificate}. The two source rows, two windows, two modulus rows, shared threshold, comparison, transport, continuation, ledger, and local name are the whole root-facing threshold surface.

Then apply \autoref{thm:regular-cauchy-tail-meet-source-window-modulus-route}. It supplies the $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ provenance for that surface, while the local $\NameCert$ row names the same finite route.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root window-modulus exactness]
\label{thm:regular-cauchy-tail-meet-root-window-modulus-exactness}
For an accepted $\RegularCauchyTailMeetUp$ packet, the paired window rows $W_0,W_1$ and source modulus rows $M_0,M_1$ are exactly the route to the shared dyadic threshold $\tau$. Any root-facing threshold read reaches $\tau$ through the source-window-modulus route and the shared-threshold route determinacy.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regular-cauchy-tail-meet-source-window-modulus-route} to factor a threshold read through the paired window rows and source modulus rows. This gives the displayed route to the dyadic threshold ledger.

Apply \autoref{thm:regular-cauchy-tail-meet-shared-threshold-route-determinacy}. A second root-facing read with the same transported windows and modulus rows reaches the same threshold ledger, so the paired window and modulus rows are the exact route to $\tau$.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root consumer export boundary]
\label{thm:regular-cauchy-tail-meet-root-consumer-export-boundary}
Downstream $\RealUp$ and $\UniformCauchyCriterionUp$ consumers of an accepted $\RegularCauchyTailMeetUp$ packet receive only the finite threshold packet
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
They receive no quotient stream, selected limit, host equality, trichotomy, or ambient completeness row.
\end{theorem}
\begin{proof}
Use \autoref{thm:regular-cauchy-tail-meet-root-consumer-exhaustion}. It confines downstream consumers to the two-tail, one-threshold ledger and excludes quotient, selected-limit, host-equality, trichotomy, and completeness rows.

Then use \autoref{thm:regular-cauchy-tail-meet-root-threshold-provenance} and \autoref{thm:regular-cauchy-tail-meet-root-window-modulus-exactness}. These identify the exported ledger with the displayed finite packet and route both $\RealUp$ and $\UniformCauchyCriterionUp$ reads through the same threshold surface.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root seal-budget totality]
\label{thm:regular-cauchy-tail-meet-root-seal-budget-totality}
Every admitted root-facing $\RealUp$ seal-budget read of an accepted $\RegularCauchyTailMeetUp$ packet is total on the displayed shared-threshold route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The read must pass through the paired $\RegSeqRatUp$ source rows, paired $\StreamNameUp$ windows, paired source modulus rows, the shared $\DyadicRatCoreUp$ threshold ledger, and the local $\NameCert$ rows before the seal-budget consumer sees the packet.
\end{theorem}
\begin{proof}
Start with root carrier admission and root threshold source ledger. These results expose the paired sources, windows, modulus rows, shared threshold, comparison row, transports, continuations, ledger, and local name as the whole root-facing route.

Use real-seal route totality. It places every $\RealUp$ seal read behind the same tail-meet window and dyadic endpoint rows, so an admitted seal-budget read has a displayed route whenever the root packet is accepted.

Finally apply root consumer export boundary. The exported data are exactly the finite threshold packet, and no quotient stream, selected limit, host equality, trichotomy, or ambient completeness row is supplied to complete the read elsewhere.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root tail-comparison admission]
\label{thm:regular-cauchy-tail-meet-root-tail-comparison-admission}
A root consumer may admit the $\RegularCauchyTailMeetUp$ tail comparison only through the paired $\RegSeqRatUp$ sources, paired $\StreamNameUp$ windows, paired source modulus rows, shared $\DyadicRatCoreUp$ threshold, comparison row $Q$, componentwise $\hsame$ transports, displayed $\Cont$ replay, finite ledger, provenance, and local $\NameCert$ rows of the carrier.

The admission surface is stable under the same transported source, window, and modulus rows, and it has no independent tail oracle, selected subsequence, quotient stream equality, or ambient completeness premise.
\end{theorem}
\begin{proof}
Project the comparison through root classifier stability. The classifier uses the displayed paired-window route to $\tau$ and $Q$, and componentwise transport preserves that route.

Apply source-window-modulus route and shared-threshold route determinacy. They force a root comparison read through the paired source, window, and modulus rows before it reaches the dyadic threshold ledger, and duplicate reads with the same transported route reach the same threshold.

Use window-source exhaustion and shared-threshold non-escape. These results exclude additional window sources, independent tail oracles, selected subsequences, quotient stream equality, host limits, and ambient completeness from the admitted comparison surface.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root formal handoff surface]
\label{thm:regular-cauchy-tail-meet-root-formal-handoff-surface}
The root consumer package, root seal-budget totality, and root tail-comparison admission assemble the formal handoff surface for downstream $\RealUp$ and $\UniformCauchyCriterionUp$ consumers. The handoff binds the shared-threshold route to $\RealUp$ seal budgets, admits the tail comparison through $Q$, records $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ provenance, and preserves the local $\NameCert$ rows of the accepted $\RegularCauchyTailMeetUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_root\_formal\_handoff\_surface}
\begin{proof}
First collect the root consumer package. It assembles selector, seal, public shared-threshold, and bridge-facing consumers around one finite shared-threshold route.

Next add root seal-budget totality. This makes the $\RealUp$ seal-budget side total exactly on the displayed paired-source, paired-window, source-modulus, dyadic-threshold, comparison, transport, continuation, ledger, provenance, and naming rows.

Then add root tail-comparison admission. The comparison side is admitted only through the same $Q$ row and the same transported source, window, modulus, threshold, route, provenance, and local certificate data.

Finally use root consumer export boundary and root threshold provenance. They identify the exported handoff with the finite packet and record its $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\NameCert$ provenance, while excluding quotient streams, selected limits, host equality, trichotomy, and ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet selector-budget route lock]
\label{thm:regular-cauchy-tail-meet-selector-budget-route-lock}
Any $\RegularCauchySelectorBudgetUp$ read consumed by the root-facing $\RegularCauchyTailMeetUp$ formal handoff of \autoref{thm:regular-cauchy-tail-meet-root-formal-handoff-surface} must pass through the same paired $\RegSeqRatUp$ sources, paired $\StreamNameUp$ windows, source modulus rows, shared $\DyadicRatCoreUp$ threshold ledger, comparison row, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row displayed by the accepted TailMeet packet before it reaches any $\RealUp$ seal.

The selector-budget sibling of \autoref{ch:concrete-instances-regularcauchyselectorbudget-namecert} contributes only finite-window and $\RegSeqRatUp$ readback along that route. It supplies no second selector, quotient stream, host limit, selected subsequence, or ambient completeness coordinate beyond the root seal-budget and tail-comparison surfaces of \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-totality} and \autoref{thm:regular-cauchy-tail-meet-root-tail-comparison-admission}.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_selector\_budget\_route\_lock}
\begin{proof}
Begin with the root formal handoff surface. By \autoref{thm:regular-cauchy-tail-meet-root-formal-handoff-surface}, the downstream handoff is already the finite packet whose source, window, modulus, threshold, comparison, transport, route, provenance, and local certificate rows are displayed by the accepted $\RegularCauchyTailMeetUp$ carrier.

Apply \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-totality}. Any $\RealUp$ seal-budget read behind that handoff is total only on the displayed TailMeet route, so a selector-budget read consumed by the seal side cannot bypass the paired sources, windows, modulus rows, threshold ledger, $Q$ row, transports, continuations, provenance, or local name.

Apply \autoref{thm:regular-cauchy-tail-meet-root-tail-comparison-admission}. The comparison side is admitted through the same transported rows, and the admission excludes an independent tail oracle, selected subsequence, quotient stream equality, and ambient completeness premise.

Finally read the sibling route through \autoref{ch:concrete-instances-regularcauchyselectorbudget-namecert}. That chapter supplies the finite-window and $\RegSeqRatUp$ readback needed by the selector-budget consumer, and the preceding TailMeet rows lock that contribution to the root packet before any $\RealUp$ seal receives it.
\end{proof}
