\begin{theorem}[RegularCauchyTailMeet root window threshold coverage]
\label{thm:regular-cauchy-tail-meet-root-window-threshold-coverage}
Every root consumer request for an accepted $\RegularCauchyTailMeetUp$ packet reaches the shared threshold only through
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau
$$
together with the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The request has no route to the threshold outside the paired source rows, paired window rows, source-modulus rows, and finite transport/provenance surface.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_root\_window\_threshold\_coverage}
\begin{proof}
Start with window-source coverage. The coverage theorem forces every threshold-facing read to expose the two source rows and the two window rows before the shared threshold can be read.

Next use source-modulus exhaustion. It attaches the two modulus rows $M_0,M_1$ to the same route and leaves no separate modulus source for a root consumer request.

Finally apply shared-threshold non-escape and consumer exactness. The displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows are therefore the only structural rows through which the threshold is transported to a root consumer.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root modulus route exactness]
\label{thm:regular-cauchy-tail-meet-root-modulus-route-exactness}
For an accepted $\RegularCauchyTailMeetUp$ packet, the source-modulus rows are the only admissible route into the shared-threshold ledger. A root threshold read is admitted exactly when it factors through the source-window-modulus route, the shared-threshold transport, and the displayed non-escape boundary.
\end{theorem}
\begin{proof}
Apply ledger exactness first. The shared threshold ledger has only the displayed dyadic threshold coordinate, so a proposed route cannot enter the ledger through an unlisted analytic row.

Next compose with shared-threshold transport. Transport moves the paired source, window, modulus, threshold, comparison, ledger, package, and local naming rows together, preserving the same threshold row for root reads.

Finally use the non-escape exclusions. Since quotient streams, selected limits, trichotomy rows, host equality, and ambient completeness are absent from the carrier, the source-modulus rows are the exact route into the threshold ledger.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root Real seal consumer exhaustion]
\label{thm:regular-cauchy-tail-meet-root-real-seal-consumer-exhaustion}
Any $\RegSeqRatUp$ or $\RealUp$ root consumer of an accepted $\RegularCauchyTailMeetUp$ packet reads the finite tail-meet packet before any seal row is consumed. The consumer receives no quotient stream, selected limit, trichotomy row, host equality row, or ambient completeness row.
\end{theorem}
\leanvariant{BEDC.Derived.RegularCauchyTailMeetUp.RegularCauchyTailMeetPacket\_root\_downstream\_seal\_route}
\begin{proof}
First apply root window threshold coverage. It routes the root consumer through $R_0,R_1,W_0,W_1,M_0,M_1,\tau$ and the displayed structural rows before the threshold is available.

Next apply root modulus route exactness. The source-modulus route is the only entrance into the threshold ledger, so a regular-rational or real-facing consumer cannot bypass the finite tail-meet packet.

Finally compose with the Real seal handoff and the public shared-threshold certificate. The handoff places seal consumption after the finite packet, while the public certificate exposes only the shared threshold surface and none of quotient streams, selected limits, trichotomy, host equality, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root observation-budget entry]
\label{thm:regular-cauchy-tail-meet-root-observation-budget-entry}
For an accepted $\RegularCauchyTailMeetUp$ packet, a root threshold read can enter the finite $\RealObservationBudgetUp$ surface of \autoref{ch:concrete-instances-real-observation-budget-namecert} only through the paired source, window, modulus, and threshold rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau
$$
together with the displayed comparison, transport, continuation, provenance, ledger, and local $\NameCert$ rows. No budget entry route is supplied outside this finite TailMeet packet.
\end{theorem}
\begin{proof}
Start with root window threshold coverage. It forces every root-facing read to expose the two source rows, two window rows, source modulus rows, shared threshold, and displayed structural rows before the threshold can be consumed.

Next apply root modulus route exactness. The source-modulus rows are the only admissible route into the shared-threshold ledger, so a budget entry cannot bypass $R_0,R_1,W_0,W_1,M_0,M_1,\tau$.

Finally read the target surface through \autoref{ch:concrete-instances-real-observation-budget-namecert}. That chapter admits only finite observation-budget rows, so the TailMeet threshold enters it through the displayed packet and not through quotient streams, host equality, selected limits, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root threshold readback determinacy]
\label{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy}
For an accepted $\RegularCauchyTailMeetUp$ packet, any two root threshold readbacks that use the same displayed source-window-modulus route reach the same dyadic threshold row $\tau$. The determinacy is read through
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
and through the finite observation-budget entrance of \autoref{ch:concrete-instances-real-observation-budget-namecert}.
\end{theorem}
\begin{proof}
First use root window threshold coverage to place both readbacks on the paired source rows, paired window rows, source modulus rows, and shared threshold row.

Next use root modulus route exactness. Since the source-window-modulus route is the exact entrance to the threshold ledger, two readbacks with the same displayed route cannot reach different dyadic threshold rows inside the finite packet.

Now apply root observation-budget entry. When the readback is served to $\RealObservationBudgetUp$, the budget side receives only the same displayed TailMeet rows, so it cannot split the dyadic readback by adding a quotient stream, selected limit, host equality, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root seal consumer boundary]
\label{thm:regular-cauchy-tail-meet-root-seal-consumer-boundary}
Every $\RealUp$ or $\CompletionUp$ seal consumer of an accepted $\RegularCauchyTailMeetUp$ packet is bounded by the finite observation-budget surface reached from the root threshold route. The consumer can read only the TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
and the finite $\RealObservationBudgetUp$ rows admitted by \autoref{ch:concrete-instances-real-observation-budget-namecert}; it receives no quotient stream, host equality, selected limit, trichotomy row, or ambient completeness row.
\end{theorem}
\begin{proof}
Begin with root Real seal consumer exhaustion. A $\RegSeqRatUp$ or $\RealUp$ root consumer must read the finite TailMeet packet before any seal row is consumed.

Apply root observation-budget entry and root threshold readback determinacy. Together they route the threshold through the finite observation-budget entrance and make the dyadic readback determined by the displayed source-window-modulus route.

For a $\CompletionUp$ seal consumer, use the same budgeted boundary: it receives the TailMeet threshold only after the observation-budget surface has been displayed. Since both the TailMeet packet and the observation-budget packet are finite NameCert surfaces, no quotient stream, host equality, selected limit, trichotomy row, or ambient completeness row is available to the consumer.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root seal budget synchronization]
\label{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization}
For an accepted $\RegularCauchyTailMeetUp$ packet, any root seal read synchronizes the finite threshold route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
with the finite $\RealObservationBudgetUp$ entrance before any $\RealUp$ or $\CompletionUp$ seal consumer can read the seal. The consumer therefore sees the shared dyadic threshold only through the displayed TailMeet packet and the finite observation-budget rows, with no route through quotient streams, selected limits, host equality, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
First apply root window threshold coverage and root modulus route exactness. These results put every root threshold read on the paired source rows, paired window rows, source-modulus rows, shared threshold row, rational comparison row, transport row, continuation row, ledger row, and local naming row.

Next apply root observation-budget entry. The same finite route is the only entrance into the $\RealObservationBudgetUp$ surface, so the seal-side consumer cannot receive $\tau$ before the observation-budget packet has been displayed.

Use root threshold readback determinacy to identify all readbacks along that route with the same dyadic threshold row. The budget entrance therefore carries a single determined TailMeet threshold rather than a separate consumer-side threshold.

Finally apply root seal consumer boundary. It places both $\RealUp$ and $\CompletionUp$ seal reads after the finite budgeted route and excludes quotient streams, selected limits, host equality, trichotomy rows, and ambient completeness from the seal consumer surface.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet observation-budget selector handoff]
\label{thm:regular-cauchy-tail-meet-observation-budget-selector-handoff}
For an accepted $\RegularCauchyTailMeetUp$ packet whose root threshold route is exported to a $\FiniteObservationBudgetSelectorUp$ consumer, the exported route first factors through the same finite TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N
$$
and then through the selector route
$$
B \to S \to W \to D \to R \to E.
$$
The handoff exports no quotient stream, selected limit, host real equality, trichotomy row, countable-choice row, hidden selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
First place the exported read on the finite observation-budget surface. By \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry}, the TailMeet route enters the $\RealObservationBudgetUp$ side only through $R_0,R_1,W_0,W_1,M_0,M_1,\tau$ and the displayed comparison, transport, continuation, provenance, ledger, and local naming rows.

Next identify the threshold consumed by the selector-facing export. By \autoref{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy}, every readback along the displayed route reaches the same dyadic threshold row $\tau$. By \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization}, that determined threshold is synchronized with the finite budget entrance before any $\RealUp$ or $\CompletionUp$ seal read is available.

It remains to describe the selector side of the handoff. By \autoref{thm:finite-observation-budget-selector-budget-route-determinacy}, an accepted $\FiniteObservationBudgetSelectorUp$ packet with the displayed budget rows determines one finite route $B \to S \to W \to D \to R \to E$. By \autoref{thm:finite-observation-budget-selector-diagonal-consumer-boundary}, diagonal-limit and Real-completion consumers may use that finite route but receive no independent completion principle from the selector.

Combining the two surfaces gives a single finite export: the TailMeet root threshold is read through $R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N$ and is then consumed through $B \to S \to W \to D \to R \to E$. None of the excluded analytic rows is present on either side of the handoff, so none can be exported.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet ObservationBudgetLimiter cap synchronization]
\label{thm:regular-cauchy-tail-meet-observation-budget-limiter-cap-synchronization}
For an accepted $\RegularCauchyTailMeetUp$ packet whose root threshold route is exported through $\RealObservationBudgetUp$ and then consumed by an accepted $\ObservationBudgetLimiterUp$ packet, the limiter cap row is synchronized with the same finite TailMeet route
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
Every downstream $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompletionUp$, or $\FiniteObservationBudgetSelectorUp$ read must pass first through the TailMeet source-window-modulus threshold route and then through the limiter triad
$$
(E,B,K)\quad (W,D,R)\quad (S,H,C,P,N).
$$
The synchronized handoff exports no quotient stream, selected limit, host real equality, trichotomy row, hidden selector, uncapped schedule, independent $\RealUp$ carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
First fix the TailMeet side of the export. Apply \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry} to place the root threshold entrance inside $\RealObservationBudgetUp$ on the displayed source, window, modulus, threshold, comparison, transport, continuation, ledger, and local naming rows. Then apply \autoref{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy} and \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization}. These identify every readback along that route with the same dyadic threshold row and the same finite budget entrance.

Next read the limiter side through \autoref{ch:concrete-instances-observationbudgetlimiter-namecert}. By \autoref{thm:observation-budget-limiter-budget-cap-totality}, the accepted limiter packet admits a cap row $K$ only after the request and observation-budget rows $E,B$ and before any served window row. By \autoref{thm:observation-budget-limiter-window-readback-exactness}, the downstream readback rows $W,D,R$ remain tied to that same capped route.

Finally combine this limiter boundary with \autoref{thm:regular-cauchy-tail-meet-observation-budget-selector-handoff} and \autoref{thm:observation-budget-limiter-service-triad-coverage}. The first theorem shows that selector-facing reads consume the TailMeet threshold only through the finite observation-budget route, while the second identifies the public limiter service as the triad $(E,B,K)$, $(W,D,R)$, and $(S,H,C,P,N)$. Thus each listed downstream consumer must read the TailMeet route before it reads the limiter triad, and the excluded analytic rows have no carrier coordinate or local $\NameCert$ clause from which to be exported.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet budgeted refinement seal factorization]
\label{thm:regular-cauchy-tail-meet-budgeted-refinement-seal-factorization}
For an accepted $\RegularCauchyTailMeetUp$ packet, any root threshold route exported to a $\CauchyModulusRefinementUp$ consumer or to a $\CauchyLimitSealUp$ consumer is read in the following order. The consumer first reads the displayed TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
It then reads the finite observation-budget surface and any limiter cap surface attached to that route. Only after those finite rows have been displayed may a $\RealUp$ or $\CompletionUp$ consumer read the seal. The route exports no quotient stream, selected limit, host real equality, trichotomy row, hidden selector, uncapped observation schedule, independent completion carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with the root threshold route. By \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry}, every accepted export enters the $\RealObservationBudgetUp$ surface only through the displayed TailMeet rows, together with their comparison, transport, continuation, ledger, and local naming coordinates.

The threshold row is then fixed before the seal is visible. Apply \autoref{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy} to identify all readbacks along the route with the same dyadic threshold row $\tau$, and apply \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization} to place the $\RealUp$ and $\CompletionUp$ seal reads after the finite budget entrance.

Now attach the capped budget surface. By \autoref{thm:regular-cauchy-tail-meet-observation-budget-limiter-cap-synchronization}, every downstream $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompletionUp$, or selector-facing read must pass through the TailMeet route and then through the limiter service rows before it can consume a seal.

Finally compare the two named consumers. The refinement chapter \autoref{ch:concrete-instances-cauchy-modulus-refinement-namecert} reads a Real or Completion route only after its displayed source, selector-budget, window, readback, and seal rows are present, while the Cauchy-limit seal chapter \autoref{ch:concrete-instances-cauchylimitseal-namecert} records the finite seal handoff boundary. Composing these chapter surfaces with the TailMeet budget and limiter theorems gives the stated factorization and leaves none of the excluded analytic rows with a carrier coordinate from which to be exported.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet root budget-limiter factorization]
\label{thm:regular-cauchy-tail-meet-root-budget-limiter-factorization}
For an accepted $\RegularCauchyTailMeetUp$ packet, any root threshold route exported to $\RealObservationBudgetUp$, $\ObservationBudgetLimiterUp$, $\CauchyModulusRefinementUp$, or $\CauchyLimitSealUp$ factors in one order. The route first reads the displayed TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
It then enters the finite observation-budget surface, then passes through the limiter cap and service triad, before any $\RealUp$ or $\CompletionUp$ seal is read. The route exports no quotient stream, selected limit, host real equality, trichotomy row, hidden selector, uncapped observation schedule, independent completion carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
First place the root route on the TailMeet packet. By \autoref{thm:regular-cauchy-tail-meet-root-observation-budget-entry}, every threshold export reaches $\RealObservationBudgetUp$ only through the paired source, window, modulus, threshold, comparison, transport, continuation, ledger, and local naming rows.

Next fix the threshold readback. The determinacy theorem \autoref{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy} identifies all readbacks along that displayed route with the same dyadic threshold row $\tau$, and \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization} synchronizes that threshold with the finite budget entrance before any $\RealUp$ or $\CompletionUp$ seal is available.

Now attach the limiter stage. By \autoref{thm:regular-cauchy-tail-meet-observation-budget-limiter-cap-synchronization}, the downstream read must pass from the TailMeet route into the limiter cap and service triad $(E,B,K)$, $(W,D,R)$, and $(S,H,C,P,N)$.

Finally apply the budgeted refinement seal factorization, \autoref{thm:regular-cauchy-tail-meet-budgeted-refinement-seal-factorization}. It places $\CauchyModulusRefinementUp$ and $\CauchyLimitSealUp$ after the displayed TailMeet rows, finite observation-budget entrance, and capped limiter service, leaving no excluded analytic coordinate from which a Real or Completion seal can be read earlier.
\end{proof}

\begin{theorem}[RegularCauchyTailMeet limit seal window pullback]
\label{thm:regular-cauchy-tail-meet-limit-seal-window-pullback}
For an accepted $\RegularCauchyTailMeetUp$ packet whose root threshold route is exported to an accepted $\CauchyLimitSealUp$ packet and an accepted $\RealObservationBudgetUp$ packet over the same finite $\StreamNameUp$ window, every seal-facing read pulls back to the same displayed TailMeet rows
$$
R_0,R_1,W_0,W_1,M_0,M_1,\tau,Q,H,C,L,N.
$$
The same pullback then reaches the $\StreamNameUp$ finite-window lattice meet and the displayed $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Conversely, those displayed rows repack into one consumer route for the $\CauchyLimitSealUp$ seal row and the $\RealObservationBudgetUp$ entrance. The route contains no quotient stream, selected limit, host real equality, trichotomy row, hidden selector, unbounded schedule, separate completion carrier, or ambient completeness principle.
\end{theorem}
\begin{proof}
First place the root route on the TailMeet packet. By \autoref{thm:regular-cauchy-tail-meet-root-budget-limiter-factorization}, any route exported toward $\RealObservationBudgetUp$, $\CauchyModulusRefinementUp$, or $\CauchyLimitSealUp$ must read the displayed TailMeet rows, finite observation-budget entrance, and capped limiter service before a seal is available.

Next move from the finite budget route to the seal read. Apply \autoref{thm:regular-cauchy-tail-meet-budgeted-refinement-seal-factorization} and \autoref{thm:regular-cauchy-tail-meet-root-seal-budget-synchronization}. These place every $\CauchyLimitSealUp$ or $\RealObservationBudgetUp$ consumer after the same finite threshold route and synchronize the seal-facing read with the finite budget entrance.

Now identify the shared $\StreamNameUp$ window. The finite-window lattice dependency of \autoref{thm:cauchy-limit-seal-finite-window-lattice-dependency} forces the seal-facing route through the $\StreamNameUp$ finite-window meet, and the tail-budget meet of \autoref{thm:cauchy-limit-seal-tail-budget-meet} identifies that meet with the displayed regular source, dyadic ledger, real seal, transport, continuation, provenance, and local naming rows.

For the converse direction, start with exactly those displayed TailMeet, stream-window, regular-source, dyadic, real, transport, continuation, package, and naming rows. The cited finite-window and tail-budget meet theorems repack them as the $\CauchyLimitSealUp$ seal row together with the $\RealObservationBudgetUp$ entrance, while the TailMeet budget-limiter factorization supplies the root consumer route.

Finally use \autoref{thm:regular-cauchy-tail-meet-root-threshold-readback-determinacy}. It identifies all readbacks along the displayed route with the same threshold row $\tau$, so the forward pullback and the reverse repacking describe one deterministic route and none of the excluded analytic rows has a coordinate from which to enter it.
\end{proof}
