\section{The certificate}
\label{sec:manifold-certificate}

\begin{theorem}[Manifold chart endpoint coverage]
\label{thm:manifold-chart-endpoint-coverage}
For a charted carrier package $\mathcal{M}$ as in
\autoref{def:manifold-charted-carrier}, every displayed chart row exposes the
following endpoint data:
\begin{enumerate}
\item the underlying $\TopologyUp$ carrier row $X(x)$ and the classifier
$\mathsf{same}_X$ supplied by $\mathcal{T}$;
\item the witnessed open row
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(a),\mathsf{Dom}_a)$ for the
chart domain;
\item the finite $\RealUp$ coordinate output
$\mathsf{coord}_a(x)=(r_1,\ldots,r_{n(a)})$;
\item the visible atlas ledger entry recording $a$, $\mathsf{domIx}(a)$,
$x$, and the coordinate list.
\end{enumerate}
\end{theorem}
\begin{proof}
Unfold the charted carrier package of
\autoref{def:manifold-charted-carrier}. The first fields are exactly the
predicate $X$ on $\mathsf{BHist}$ and the indexed open topology carrier
$\mathcal{T}$, so the $\TopologyUp$ carrier and classifier are obtained by
projection.

For a fixed atlas index $a$, the same unfolding exposes the domain predicate
$\mathsf{Dom}_a$, the chosen open index $\mathsf{domIx}(a)$, and the carrying
equation for that open. This is the chart-domain open witness required by the
certificate.

Finally project the chart map field. Its output is already a finite list of
$\RealUp$ coordinate histories, and the atlas index plus open index are
retained in the package ledger. No quotient or hidden atlas representative is
introduced, so the displayed tuple is the visible readback of the chart row.
\end{proof}

\begin{theorem}[Manifold transition classifier stability]
\label{thm:manifold-transition-classifier-stability}
Let $\mathcal{M}$ be a charted carrier package. Suppose $x,y:\mathsf{BHist}$
are carried points with $\mathsf{same}_X(x,y)$, and suppose the atlas domains
$\mathsf{Dom}_a$ and $\mathsf{Dom}_b$ carry $x$ through their witnessed open
indices. Then the overlap transition row
$\mathsf{Trans}_{a,b}(x)$ transports to the corresponding row at $y$ using:
\begin{enumerate}
\item the topology carrier classifier and membership-stability field of
\autoref{def:topology-indexed-open-carrier};
\item the two carrying equations for
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(a),\mathsf{Dom}_a)$ and
$\mathsf{CarriesOpen}_{\mathcal{T}}(\mathsf{domIx}(b),\mathsf{Dom}_b)$;
\item the $\RealUp$ classifier on each coordinate of
$\mathsf{coord}_a(-)$ and $\mathsf{coord}_b(-)$;
\item the supplied $\RealAnalyticUp$ local transport rows from
\autoref{thm:real-analytic-certificate-boundary}.
\end{enumerate}
Consequently the transported source and target coordinate lists represent the
same overlap transition in the atlas ledger.
\end{theorem}
\begin{proof}
Begin with the topology side. The carrying equation for
$\mathsf{domIx}(a)$ converts $\mathsf{Dom}_a(x)$ into
$\mathsf{OpenAt}(\mathsf{domIx}(a),x)$. The membership-stability field of
\autoref{def:topology-indexed-open-carrier}, applied to
$\mathsf{same}_X(x,y)$, transports this open membership to $y$, and the same
carrying equation converts it back to $\mathsf{Dom}_a(y)$.

Repeat the identical argument for $b$. This supplies the transported overlap
witness $\mathsf{Dom}_a(y)\wedge\mathsf{Dom}_b(y)$, so the transition ledger
has the same atlas indices at the transported point.

Project the coordinate fields from
\autoref{def:manifold-charted-carrier}. Their stability clauses give
coordinatewise $\RealUp$ classifier witnesses from
$\mathsf{coord}_a(x)$ to $\mathsf{coord}_a(y)$ and from
$\mathsf{coord}_b(x)$ to $\mathsf{coord}_b(y)$.

The transition row itself is one of the real-analytic rows supplied at the
boundary of \autoref{thm:real-analytic-certificate-boundary}. Apply that row
to the transported overlap witness and the coordinatewise $\RealUp$ classifier
witnesses. The result is the transition row at $y$, classified by the same
visible atlas ledger entry.
\end{proof}

\begin{theorem}[Manifold charted NameCert surface]
\label{thm:manifold-charted-namecert-surface}
A charted carrier package $\mathcal{M}$ as in
\autoref{def:manifold-charted-carrier}, together with
\autoref{thm:manifold-chart-endpoint-coverage} and
\autoref{thm:manifold-transition-classifier-stability}, assembles the
paper-side $\NameCert_{\ManifoldUp}$ obligation surface. Its fields are the
$\mathsf{BHist}$ point carrier $X$, the $\TopologyUp$ classifier
$\mathsf{same}_X$, the finite atlas ledger, chart-domain open witnesses,
finite $\RealUp$ coordinate outputs, overlap-transition stability rows, and an
explicit statement that no standard bridge is claimed.
\end{theorem}
\begin{proof}
Unfold the NameCert template fields against
\autoref{def:manifold-charted-carrier}. The traditional target is a charted
manifold, the BEDC source is $\mathsf{BHist}$ equipped with the topology
carrier $\mathcal{T}$ and the finite atlas data, the carrier is $X$, and the
classifier is $\mathsf{same}_X$.

Endpoint coverage supplies the public readback rows: each chart exposes its
carried point, witnessed open domain, finite coordinate output, and atlas
ledger entry. These are exactly the carrier, source, and ledger fields needed
by the certificate surface.

Transition classifier stability supplies the stability field. It transports
overlap rows along the topology classifier, uses the two chart-domain carrying
equations to keep the point inside both domains, and then invokes the
$\RealUp$ and $\RealAnalyticUp$ rows for coordinate and smooth-transition
transport.

The exactness policy is visible-ledger exactness: a manifold chart row is
accepted only through the displayed atlas index, open witness, coordinate
output, and transition row. The standard bridge field is absent, so the
assembled surface is a BEDC paper-side NameCert obligation package rather than
a bridge to an external manifold library.
\end{proof}

\begin{theorem}[Manifold chart-transition classifier stability]
\label{thm:manifold-chart-transition-classifier-stability}
Let $P$ and $Q$ be $\mathsf{BHist}$ packages. Suppose
$\mathsf{ManAtlasPkg}(P)$ holds and the data of $P$ and $Q$ are related
componentwise by $\hsame$: the topological carrier histories are $\hsame$, the
finite chart-index histories are $\hsame$, corresponding chart-domain rows are
$\hsame$, corresponding chart-map rows are $\hsame$, and corresponding
real-analytic transition ledgers are $\hsame$. Then
$\mathsf{ManAtlasPkg}(Q)$ holds.
\end{theorem}
\begin{proof}
Unpack $\mathsf{ManAtlasPkg}(P)$ using
\autoref{def:manifold-chart-atlas-carrier}. The package supplies the
$\TopologyUp$ carrier row for $M$, the finite chart-index row, all chart-domain
and chart-map rows, and the overlap transition ledgers.

Transport the topological carrier by the supplied $\hsame$ comparison of the
carrier histories. Transport the finite chart-index row in the same way. For
each chart index, transport the domain predicate and the chart-map row by the
componentwise $\hsame$ hypotheses.

For each chart pair, transport the real-coordinate transition ledger and the
constructively smooth transition certificate by the corresponding
real-analytic $\hsame$ row. Repack the transported topology, chart, map,
overlap, and smoothness rows. These are exactly the fields required by
\autoref{def:manifold-chart-atlas-carrier} for
$\mathsf{ManAtlasPkg}(Q)$.
\end{proof}

\begin{theorem}[ManifoldUp transition ledger stability]
\label{thm:manifoldup-transition-ledger-stability}
Let $P$ and $Q$ be $\mathsf{BHist}$ packages. Suppose
$\mathsf{ManAtlasPkg}(P)$ holds and the atlas rows of $P$ and $Q$ are related
componentwise by $\hsame$: the carrier histories, finite chart-index histories,
indexed-open domain rows, coordinate histories, and real-analytic transition
ledgers are all related. Then the transition ledger of $P$ transports to a
transition ledger for $Q$.
\end{theorem}
\begin{proof}
Start with a displayed transition row of $P$ for chart indices $i,j$. It
contains the overlap membership boundary, the coordinate-change history, and
the $\RealAnalyticUp$ local transition certificate.

Transport the two chart-domain rows by componentwise $\hsame$. The
$\TopologyUp$ indexed-open membership stability clause transports the overlap
predicate because it is the conjunction of the two transported domain
memberships.

Transport the source and target coordinate histories by their componentwise
$\hsame$ rows. The real-analytic transport boundary then carries the local
transition certificate across the transported coordinate histories.

Repack the transported overlap, coordinate-change history, and real-analytic
certificate. The result is the corresponding transition ledger row for $Q$.
\end{proof}

\begin{theorem}[Manifold atlas overlap coverage]
\label{thm:manifold-atlas-overlap-coverage}
Every carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$ exposes, for
each chart pair $i,j$ in its finite chart-index history, a domain-overlap row
$$
\mathsf{Overlap}_{ij}(x)
:\Longleftrightarrow
\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_j(x)
$$
on the topological carrier and the corresponding constructively smooth
$\RealUp$ transition ledger from $\varphi_i$-coordinates to
$\varphi_j$-coordinates on that overlap.
\end{theorem}
\begin{proof}
Unpack the carried atlas package by
\autoref{def:manifold-chart-atlas-carrier}. The finite chart-index row gives
the admissible chart pairs, while the chart-domain rows give the two predicates
$\mathsf{Dom}_i$ and $\mathsf{Dom}_j$ over the same topological carrier.

For a fixed pair $i,j$, form the overlap row by conjunction of the two domain
memberships. The topology ledger records the carrier support of both domains,
so the overlap row is a predicate on the same topological carrier $M$.

The package ledger contains, for this same pair, the transition row
$\mathsf{Trans}_{ij}$. Its real-coordinate part records the source and target
$\RealUp$ coordinate histories, and its real-analytic part records the
constructively smooth transition certificate on the displayed overlap. Project
these two ledger components to obtain the claimed coverage row.
\end{proof}

\begin{definition}[Manifold transition coherence ledger]
\label{def:manifold-transition-coherence-ledger}
For a carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$, the transition
coherence ledger is the sub-ledger of $\mathsf{ManAtlasPkg}(P)$ whose rows are
indexed by one, two, and three chart names in the finite chart-index history.
It contains the following displayed entries.
\begin{enumerate}
\item For every chart $i$, the row $\mathsf{IdTrans}_i$ is carried on the
self-overlap $\mathsf{Overlap}_{ii}$ supplied by $\TopologyUp$ and classifies
the transition $\mathsf{Trans}_{ii}$ by the identity coordinate history row on
$\varphi_i$.
\item For every chart pair $i,j$, the row $\mathsf{InvTrans}_{ij}$ is carried
on the overlap transported between $\mathsf{Overlap}_{ij}$ and
$\mathsf{Overlap}_{ji}$ by the $\TopologyUp$ overlap rows, and classifies the
two composites $\mathsf{Trans}_{ji}\circ\mathsf{Trans}_{ij}$ and
$\mathsf{Trans}_{ij}\circ\mathsf{Trans}_{ji}$ by the corresponding
$\mathsf{IdTrans}$ rows.
\item For every chart triple $i,j,k$, the row $\mathsf{Cocycle}_{ijk}$ is
carried on the triple-overlap predicate
$$
\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_j(x)\wedge\mathsf{Dom}_k(x),
$$
and classifies $\mathsf{Trans}_{jk}\circ\mathsf{Trans}_{ij}$ and
$\mathsf{Trans}_{ik}$ by the same real-analytic transition row from
$\varphi_i$-coordinates to $\varphi_k$-coordinates.
\end{enumerate}
Each entry is a visible ledger row over $\TopologyUp$ carried-overlap
transport, $\RealUp$ coordinate histories, and the real-analytic classifier
rows already exposed by the atlas package.
\end{definition}

\begin{theorem}[Manifold overlap identity transition]
\label{thm:manifold-overlap-identity-transition}
Every carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$ exposes, for
each chart $i$, a self-overlap transition row $\mathsf{Trans}_{ii}$ on
$\mathsf{Overlap}_{ii}$. This row is classified by $\mathsf{IdTrans}_i$ in the
transition coherence ledger, so its coordinate action is the identity
real-coordinate row on $\varphi_i$ over the carried self-overlap.
\end{theorem}
\begin{proof}
Unpack $\mathsf{ManAtlasPkg}(P)$ by
\autoref{def:manifold-chart-atlas-carrier}. The finite chart-index row admits
the pair $(i,i)$, and \autoref{thm:manifold-atlas-overlap-coverage} identifies
the carried domain as $\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_i(x)$ on the
underlying $\TopologyUp$ carrier.

Project the self row from
\autoref{def:manifold-transition-coherence-ledger}. Its source and target
coordinate histories are both the displayed list $\varphi_i(x)$, transported
through the same carried-overlap row.

The real-analytic classifier component of $\mathsf{IdTrans}_i$ is the identity
coordinate row. Repacking that classifier with the self-overlap transport gives
the displayed $\mathsf{Trans}_{ii}$ transition classified as the identity on
$\varphi_i$.
\end{proof}

\begin{theorem}[Manifold overlap inverse transition]
\label{thm:manifold-overlap-inverse-transition}
Every carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$ exposes, for
each chart pair $i,j$, inverse transition rows on the carried overlap. The
composite $\mathsf{Trans}_{ji}\circ\mathsf{Trans}_{ij}$ is classified by
$\mathsf{IdTrans}_i$ on the $i$-coordinate overlap, and the composite
$\mathsf{Trans}_{ij}\circ\mathsf{Trans}_{ji}$ is classified by
$\mathsf{IdTrans}_j$ on the $j$-coordinate overlap.
\end{theorem}
\begin{proof}
Unpack the two pairwise overlap rows using
\autoref{thm:manifold-atlas-overlap-coverage}. The row for $(i,j)$ carries
$\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_j(x)$, while the row for $(j,i)$ carries
the same two domain memberships in the reversed order.

Use the $\TopologyUp$ carried-overlap transport to identify those two overlap
readbacks. This gives a common domain on which both transition ledgers can be
composed without changing the carried point or the chart-domain witnesses.

Project $\mathsf{InvTrans}_{ij}$ from
\autoref{def:manifold-transition-coherence-ledger}. Its real-analytic
classifier rows state exactly that the two displayed composites classify to
the relevant identity rows. Together with
\autoref{thm:manifold-overlap-identity-transition}, these projected rows give
the two claimed inverse identities on the carried overlap.
\end{proof}

\begin{theorem}[Manifold triple-overlap cocycle]
\label{thm:manifold-triple-overlap-cocycle}
Every carried atlas package $P$ with $\mathsf{ManAtlasPkg}(P)$ exposes, for
each chart triple $i,j,k$, a cocycle row on the carried triple overlap. On that
overlap, $\mathsf{Trans}_{jk}\circ\mathsf{Trans}_{ij}$ and
$\mathsf{Trans}_{ik}$ are classified by the same real-analytic transition row
from $\varphi_i$-coordinates to $\varphi_k$-coordinates.
\end{theorem}
\begin{proof}
Start from the three pairwise overlap rows supplied by
\autoref{thm:manifold-atlas-overlap-coverage}. Their $\TopologyUp$ domain
components restrict to the same carried triple-overlap predicate
$\mathsf{Dom}_i(x)\wedge\mathsf{Dom}_j(x)\wedge\mathsf{Dom}_k(x)$.

Transport the pairwise transition ledgers to this common triple-overlap
domain. The source of $\mathsf{Trans}_{ij}$ is the $\varphi_i$ coordinate row,
its target is the $\varphi_j$ row, and the source of $\mathsf{Trans}_{jk}$ is
the same $\varphi_j$ row after $\RealUp$ coordinate-history transport.

Project $\mathsf{Cocycle}_{ijk}$ from
\autoref{def:manifold-transition-coherence-ledger}. Its real-analytic
classifier component identifies the composite
$\mathsf{Trans}_{jk}\circ\mathsf{Trans}_{ij}$ with the direct transition
$\mathsf{Trans}_{ik}$ as the same transition row from $\varphi_i$ to
$\varphi_k$. Repacking that classifier with the common carried-overlap domain
gives the displayed cocycle obligation.
\end{proof}

\begin{theorem}[Manifold name-certificate obligation surface]
\label{thm:manifold-namecert-obligation-surface}
The carrier definition of
\autoref{def:manifold-chart-atlas-carrier}, together with
\autoref{thm:manifold-chart-transition-classifier-stability} and
\autoref{thm:manifold-atlas-overlap-coverage},
\autoref{thm:manifold-overlap-identity-transition},
\autoref{thm:manifold-overlap-inverse-transition}, and
\autoref{thm:manifold-triple-overlap-cocycle}, assembles the paper-side
$\ManifoldUp$ obligation surface. The surface consists of a topological carrier,
a finite chart atlas, chart classifier stability, overlap coverage,
transition-smoothness rows, identity transitions, inverse transition
composites, triple-overlap cocycles, and no standard bridge row.
\end{theorem}
\begin{proof}
The carrier definition supplies the named source object:
$\TopologyUp$ rows for the base carrier, $\RealUp$ coordinate rows for chart
targets, finite chart-index data, chart domains, chart maps, and transition
ledgers.

\autoref{thm:manifold-chart-transition-classifier-stability} supplies the
classifier-stability obligation for the whole package, because every public
field is transported by the componentwise $\hsame$ classifier specified in the
carrier definition.

\autoref{thm:manifold-atlas-overlap-coverage} supplies the overlap and
transition-smoothness obligations. The absence of a standard bridge is already
part of the carrier definition.

It remains to account for atlas compatibility. The coherence ledger of
\autoref{def:manifold-transition-coherence-ledger} records the self,
reversed-pair, and triple-overlap rows. The identity row is exposed by
\autoref{thm:manifold-overlap-identity-transition}; the inverse composite rows
are exposed by \autoref{thm:manifold-overlap-inverse-transition}; and the
triple-overlap cocycle row is exposed by
\autoref{thm:manifold-triple-overlap-cocycle}.

These rows use the same $\TopologyUp$ carried-overlap transport, the same
$\RealUp$ coordinate histories, and the same real-analytic classifier ledger as
the pairwise transition rows. Repacking them with the carrier, classifier, and
stability fields gives exactly the $\ManifoldUp$ paper obligation surface
listed in the theorem statement.
\end{proof}

\begin{theorem}[Manifold name-certificate obligation threshold]
\label{thm:manifoldup-namecert-obligation-threshold}
The carrier definition of
\autoref{def:manifold-chart-atlas-carrier}, together with
\autoref{thm:manifoldup-chart-cover-coverage},
\autoref{thm:manifoldup-chart-domain-carrier-transport},
\autoref{thm:manifoldup-atlas-transition-composition}, and
\autoref{thm:manifoldup-transition-ledger-stability}, assembles the paper-side
$\ManifoldUp$ $\NameCert$ obligation threshold. The threshold consists of the
carrier, classifier, chart cover, chart-domain transport, transition
composition, transition-ledger stability, and the visible atlas ledger.
\end{theorem}
\begin{proof}
The carrier definition supplies the named source object:
$\TopologyUp$ rows for the base carrier, $\RealUp$ coordinate rows for chart
targets, finite chart-index data, indexed-open chart domains, coordinate
histories, and transition ledgers.

\autoref{thm:manifoldup-chart-cover-coverage} supplies the cover obligation by
projecting, for every carried point, an index and domain membership from the
visible atlas ledger.

\autoref{thm:manifoldup-chart-domain-carrier-transport} supplies the
classifier boundary for chart-domain membership. The same componentwise
$\hsame$ classifier transports the carrier, domains, coordinate histories, and
ledger rows named in the definition.

\autoref{thm:manifoldup-atlas-transition-composition} supplies the atlas
composition obligation, and
\autoref{thm:manifoldup-transition-ledger-stability} supplies stability of the
visible transition ledger under transported chart rows. The absence of a
standard bridge is already part of the carrier definition, so the assembled
object is exactly the $\ManifoldUp$ $\NameCert$ obligation threshold listed in
the theorem statement.
\end{proof}

\begin{closurestatus}{\ManifoldUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The singleton empty-chart ManifoldUp certificate together with the finite-atlas paper obligation surface over $\mathsf{BHist}$, $\TopologyUp$, $\RealUp$, and $\RealAnalyticUp$.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ManifoldUp.ManifoldSingleton\_semanticNameCert}
  \bridgestatus{none}
  \notclaimed{General smooth-manifold theory, arbitrary atlas machine verification, external manifold-library equivalence, tangent bundles, forms, integration, or de Rham theorems.}
  \upgradepath{$\publicClosure$ requires a single exported ManifoldUp public theorem for the atlas interface and a checked bridge only after the standard model rows are explicitly supplied.}
\end{closurestatus}
