\chapter{A Concrete Naming Certificate for $\RegularSequenceSpaceUp$}
\label{ch:concrete-instances-regular-sequence-space-namecert}
\origin{human}

Following Bishop and Bridges on regular Cauchy sequences, the $\RegularSequenceSpaceUp$ packet records the finite carrier for a displayed space of regular sequence names rather than a single regular sequence certificate. It sits between the stream schedules of \autoref{ch:concrete-instances-streamname-namecert}, the rational regular readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the value-facing real seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[RegularSequenceSpace carrier]
\label{def:regular-sequence-space-carrier}
A $\RegularSequenceSpaceUp$ carrier is a finite $\BHist$ packet
$$
S=(X,T,Q,D,R,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $X$ is the displayed index-source row naming the finite family of regular sequence names currently admitted to the space packet.
\item $T$ is the $\StreamNameUp$ schedule row for the inspected tails and precision windows.
\item $Q$ is the $\RegSeqRatUp$ readback row for regular rational Cauchy names at those windows.
\item $D$ is the $\DyadicRatCoreUp$ scale row recording the dyadic tolerance core used by the regularity checks.
\item $R$ is the $\RealUp$ value-facing seal row reached only after $X,T,Q,D$ have stayed visible.
\item $H$ records componentwise $\hsame$ transport for the source, schedule, readback, dyadic scale, value seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a space-level sequence request through the stream schedule, regular rational readback, dyadic tolerance core, and real-facing seal.
\item $P$ is the $\Pkg$ provenance over $\RegularSequenceSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RegularSequenceSpaceUp}$ row.
\end{enumerate}
The carrier has no coordinate for an ambient complete metric space, quotient equality of real names, arbitrary choice of representatives, unrestricted sequence space, or host set of all Cauchy sequences.
\end{definition}

\begin{theorem}[RegularSequenceSpace NameCert obligations]
\label{thm:regular-sequence-space-namecert-obligations}
For every accepted $\RegularSequenceSpaceUp$ carrier $S=(X,T,Q,D,R,H,C,P,N)$, the local $\NameCert_{\RegularSequenceSpaceUp}$ surface consists exactly of space-level carrier admission through $X$, schedule exposure through $T$, regular rational readback through $Q$, dyadic tolerance exposure through $D$, real-facing value seal through $R$, componentwise $\hsame$ stability through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$. A consumer therefore reads a regular sequence space only through the finite route
$$
X,T,Q,D \longmapsto R,H,C,P,N .
$$
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:regular-sequence-space-carrier}. The source row $X$ opens the space-level family, while the schedule row $T$ and regular rational readback row $Q$ expose only displayed sequence windows.

The dyadic tolerance core $D$ supplies the regularity scale before the real-facing seal $R$ is consumed. Thus the packet reaches $\RealUp$ only after the stream, rational readback, and dyadic core rows have remained visible.

Finally replay the structural rows. Componentwise transport $H$, continuation replay $C$, provenance $P$, and local naming $N$ preserve the same finite carrier, so no ambient complete space, unrestricted sequence space, quotient of real names, or arbitrary representative choice enters the NameCert surface.
\end{proof}

\closureat{RegularSequenceSpaceUp}{seedStr}

\begin{closurestatus}{\RegularSequenceSpaceUp}
  \constructivestory{A $\RegularSequenceSpaceUp$ packet is generated from a displayed source family of regular sequence names, stream schedules, regular rational readbacks, dyadic tolerance core rows, a real-facing value seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-sequence-space-carrier} and \autoref{thm:regular-sequence-space-namecert-obligations} seed the finite space-level regular sequence carrier between stream names, rational regular readbacks, dyadic tolerance cores, and Real-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim an ambient complete metric space, quotient equality of real names, arbitrary choice of representatives, unrestricted sequence space, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, schedule routing, regular rational readback, dyadic tolerance exposure, real-facing sealing, and structural nonescape for BEDC.Derived.RegularSequenceSpaceUp.}
\end{closurestatus}
