\chapter{A Concrete Naming Certificate for $\CofinalModulusSealUp$}
\label{ch:concrete-instances-cofinal-modulus-seal-namecert}
\origin{ai}

The $\CofinalModulusSealUp$ packet realizes the cofinal-tail modulus route of \autoref{ch:visions-real-completeness} as one finite completion-seal naming surface. It sits after the shared threshold budget of \autoref{ch:concrete-instances-cofinal-tail-budget-namecert}, the tail-modulus seal route of \autoref{ch:concrete-instances-cauchy-tail-modulus-seal-namecert}, the window-budget route of \autoref{ch:concrete-instances-realwindowbudget-namecert}, and the terminal Cauchy-limit seal of \autoref{ch:concrete-instances-cauchylimitseal-namecert}. The packet is not a Real-completeness principle: it records the finite rows a consumer must expose before the Real-completion seal can be read.

\falsifiablePrediction{Every accepted CofinalModulusSealUp consumer must expose the cofinal tail budget, CauchyTailModulusSeal, RealWindowBudget, CauchyLimitSeal, RegSeqRat, StreamName, DyadicRatCore, RealUp, hsame, Cont, Pkg, and NameCert rows before any Real-completion seal read is public.}

\independenceWitness{cofinaltailbudget, cauchytailmodulusseal, realwindowbudget, cauchylimitseal, real: no sibling is bijective because each supplies only a proper route segment while CofinalModulusSealUp binds the cofinal modulus-to-seal route in one local packet.}

\begin{definition}[Cofinal modulus seal carrier]
\label{def:cofinal-modulus-seal-carrier}
A $\CofinalModulusSealUp$ carrier is a finite $\BHist$ packet
$$
S=(B,M,W,L,R,T,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\CofinalTailBudgetUp$ row fixing the shared cofinal-tail threshold;
\item $M$ is the $\CauchyTailModulusSealUp$ row that binds the shared modulus route to the tail seal;
\item $W$ is the $\RealWindowBudgetUp$ row exposing the finite observation window budget for the same route;
\item $L$ is the $\CauchyLimitSealUp$ row consumed only after $B,M,W$ have fixed the cofinal modulus route;
\item $R$ is the $\RegSeqRatUp$ handoff row reached from the displayed tail windows;
\item $T$ is the $\StreamNameUp$ finite-window row selected by the cofinal threshold and the window budget;
\item $D$ is the $\DyadicRatCoreUp$ tolerance and readback ledger attached to $T$;
\item $E$ is the $\RealUp$ seal row reached through $R,D,L$;
\item $H$ records componentwise $\hsame$ transport for the route rows and the local naming row;
\item $C$ records displayed $\Cont$ replay from $B,M,W$ through $T,D,R,L,E$;
\item $P$ is the $\Pkg$ provenance over $\CofinalTailBudgetUp$, $\CauchyTailModulusSealUp$, $\RealWindowBudgetUp$, $\CauchyLimitSealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CofinalModulusSealUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It has no coordinate for quotient stream equality, host real equality, selected limits, countable choice, an undisplayed completion seal, or ambient Real completeness.
\end{definition}
\leanchecked{BEDC.Derived.CofinalModulusSealUp.CofinalModulusSealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cofinal modulus seal NameCert obligations]
\label{thm:cofinal-modulus-seal-namecert-obligations}
For the carrier of \autoref{def:cofinal-modulus-seal-carrier}, the local $\NameCert_{\CofinalModulusSealUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission for $S=(B,M,W,L,R,T,D,E,H,C,P,N)$;
\item cofinal route synchronization, stating that $B,M,W$ expose one shared tail threshold, tail-modulus seal, and observation-window budget;
\item completion-seal handoff, stating that $L,R,T,D,E$ are read only through the synchronized cofinal route;
\item structural replay, stating that $H,C,P$ transport, replay, and source exactly the displayed coordinates;
\item non-escape, stating that every public consumer remains inside the displayed $\NameCert_{\CofinalModulusSealUp}$ row $N$ and cannot import quotient equality, host equality, selected limits, countable choice, or ambient completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier. The tuple lists the cofinal tail budget, Cauchy tail-modulus seal, Real window budget, Cauchy-limit seal, RegSeqRat handoff, StreamName window, DyadicRatCore ledger, RealUp seal, transport, continuation, provenance, and local naming rows.

Read the three route-source rows next. The $\CofinalTailBudgetUp$ sibling fixes the shared cofinal threshold, the $\CauchyTailModulusSealUp$ sibling binds the modulus route to the tail seal, and the $\RealWindowBudgetUp$ sibling exposes the finite observation window budget for the same route.

Now attach the completion-seal side. The $\CauchyLimitSealUp$ row $L$ can be consumed only after $B,M,W$ have fixed the route, and the rows $T,D,R,E$ display the StreamName, dyadic, RegSeqRat, and RealUp faces of that handoff.

The rows $H,C,P,N$ only transport, replay, source, and name the displayed packet. Since no excluded object is a coordinate of the carrier, the five obligation rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cofinal modulus seal RegSeqRat window factorization]
\label{thm:cofinal-modulus-seal-regseqrat-window-factorization}
Every $\RegSeqRatUp$ handoff accepted by $\CofinalModulusSealUp$ factors through the same $\StreamNameUp$ window row $T$ and $\DyadicRatCoreUp$ tolerance row $D$ selected by the cofinal tail budget $B$ and the $\RealWindowBudgetUp$ row $W$.
\end{theorem}
\leanchecked{BEDC.Derived.CofinalModulusSealUp.CofinalModulusSealRegSeqRatWindowFactorization}
\begin{proof}
Project the carrier of \autoref{def:cofinal-modulus-seal-carrier}. The RegSeqRat row $R$ is reached from the displayed tail windows, while $T$ is selected by the cofinal threshold and window budget and $D$ is attached to that selected window.

Apply \autoref{thm:cofinal-modulus-seal-shared-route-obligation} and \autoref{thm:cofinal-modulus-seal-window-handoff-obligation}. The shared-route theorem binds $B,M,W$ before the completion side is public, and the window-handoff theorem places $T,D,R$ behind the same $B$ and $W$ rows.

Finally use \autoref{thm:cofinal-modulus-seal-source-row-synchronization} and \autoref{thm:cofinal-modulus-seal-window-budget-exactness}. These identify the selected window and tolerance ledger as the only public window route for $R$, so a RegSeqRat handoff cannot factor through a detached StreamName, a second dyadic tolerance row, or an independent RealWindowBudget.
\end{proof}

\begin{theorem}[Cofinal modulus seal tail-budget transport]
\label{thm:cofinal-modulus-seal-tail-budget-transport}
Componentwise $\hsame$ transport in an accepted $\CofinalModulusSealUp$ packet preserves the cofinal tail budget $B$, the $\CauchyTailModulusSealUp$ row $M$, and the $\RealWindowBudgetUp$ row $W$ together as one source route.
\end{theorem}
\begin{proof}
Start with the source-row synchronization theorem. \autoref{thm:cofinal-modulus-seal-source-row-synchronization} states that $B,M,W$ are synchronized as one cofinal tail budget, Cauchy tail-modulus seal, and Real window budget before any downstream row is consumed.

Read the transport coordinate $H$ from the carrier. By the obligation surface in \autoref{thm:cofinal-modulus-seal-namecert-obligations}, $H$ records componentwise $\hsame$ transport for the displayed route rows and the local naming row, rather than a separate source selector.

The window-budget exactness theorem then fixes the downstream use of the transported source. \autoref{thm:cofinal-modulus-seal-window-budget-exactness} makes $T,D,R$ consume the same $B,W$ pair, while the shared-route obligation keeps $M$ on that source route. Thus transport preserves $B,M,W$ together and cannot move only one of the three rows.
\end{proof}

\begin{theorem}[Cofinal modulus seal NameCert route coverage]
\label{thm:cofinal-modulus-seal-namecert-route-coverage}
The local $\NameCert_{\CofinalModulusSealUp}$ route covers exactly the displayed rows
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
It cannot import quotient stream equality, host real equality, selected limits, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
First use \autoref{thm:cofinal-modulus-seal-namecert-obligations}. Its carrier admission, route synchronization, completion handoff, structural replay, and non-escape clauses are all written over the rows of \autoref{def:cofinal-modulus-seal-carrier}.

Next combine the route theorems. \autoref{thm:cofinal-modulus-seal-shared-route-obligation} fixes the source rows $B,M,W$, \autoref{thm:cofinal-modulus-seal-regseqrat-window-factorization} factors the RegSeqRat handoff through $T,D$, and \autoref{thm:cofinal-modulus-seal-tail-budget-transport} keeps source transport componentwise.

It remains to exclude external completion data. The completion non-escape theorem, \autoref{thm:cofinal-modulus-seal-completion-nonescape-obligation}, removes quotient stream equality, countable choice, selected host limits, host real equality, and ambient Real completeness from the consumer boundary. Therefore the local NameCert route covers exactly the displayed finite rows and nothing beyond them.
\end{proof}

\begin{theorem}[Cofinal modulus seal shared route obligation]
\label{thm:cofinal-modulus-seal-shared-route-obligation}
For the carrier of \autoref{def:cofinal-modulus-seal-carrier}, rows $B,M,W$ must name one shared cofinal route before $T,D,R,L,E$ are public. A completion-facing consumer may not read the StreamName, DyadicRatCore, RegSeqRat, CauchyLimitSeal, or RealUp rows from separate cofinal sources.
\end{theorem}
\begin{proof}
Project the carrier $S=(B,M,W,L,R,T,D,E,H,C,P,N)$. The source side of the packet is exactly the cofinal tail budget row $B$, the Cauchy tail-modulus seal row $M$, and the Real window budget row $W$.

Apply \autoref{thm:cofinal-modulus-seal-namecert-obligations}. Its cofinal route synchronization clause binds those three rows as one shared threshold, tail-modulus seal, and observation-window budget before the completion-seal handoff is readable.

The sibling chapters named in the introduction supply only their local route segments: $\CofinalTailBudgetUp$ supplies the budget, $\CauchyTailModulusSealUp$ supplies the modulus seal, and $\RealWindowBudgetUp$ supplies the window budget. The support rows $H,C,P,N$ preserve that same route, so $T,D,R,L,E$ cannot be public from separate sources.
\end{proof}

\begin{theorem}[Cofinal modulus seal window handoff obligation]
\label{thm:cofinal-modulus-seal-window-handoff-obligation}
Every $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ handoff exported by an accepted $\CofinalModulusSealUp$ packet reads through the same $\CofinalTailBudgetUp$ row $B$ and $\RealWindowBudgetUp$ row $W$.
\end{theorem}
\begin{proof}
Read the displayed rows in \autoref{def:cofinal-modulus-seal-carrier}. The StreamName row $T$ is selected by the cofinal threshold and window budget, the DyadicRatCore row $D$ is attached to that selected window, and the RegSeqRat row $R$ is reached from the displayed tail windows.

Apply \autoref{thm:cofinal-modulus-seal-namecert-obligations} and then \autoref{thm:cofinal-modulus-seal-shared-route-obligation}. The first theorem supplies the local certificate clauses, and the second locks $B,M,W$ as the shared source route before $T,D,R$ are public.

The introduction's StreamName, DyadicRatCore, and RegSeqRat sibling routes therefore enter the packet only through the same cofinal tail budget and Real window budget rows. Since the carrier has no second $B$ or $W$ coordinate, every handoff reads through that single pair.
\end{proof}

\begin{theorem}[Cofinal modulus seal completion non-escape obligation]
\label{thm:cofinal-modulus-seal-completion-nonescape-obligation}
No completion-facing consumer accepted by $\CofinalModulusSealUp$ can import quotient stream equality, countable choice, selected host limits, host real equality, or ambient Real completeness. The consumer boundary is the displayed route
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
\end{theorem}
\begin{proof}
First project the carrier and use \autoref{thm:cofinal-modulus-seal-namecert-obligations}. The carrier admission and non-escape clauses enumerate the public surface and exclude quotient equality, host equality, selected limits, countable choice, and ambient completeness as local NameCert coordinates.

Next apply \autoref{thm:cofinal-modulus-seal-shared-route-obligation} and \autoref{thm:cofinal-modulus-seal-window-handoff-obligation}. They force the StreamName, DyadicRatCore, and RegSeqRat handoffs through the same $B$ and $W$ rows before the CauchyLimitSeal and RealUp rows can be consumed.

Finally use the CauchyLimitSeal and RealUp sibling routes named in the introduction. Those siblings receive only the displayed finite handoff $B,M,W,T,D,R,L,E,H,C,P,N$ from this packet. Since no excluded completion principle appears in the carrier, the accepted consumer cannot escape the finite route.
\end{proof}

\begin{theorem}[Cofinal modulus seal source-row synchronization]
\label{thm:cofinal-modulus-seal-source-row-synchronization}
Every accepted $\CofinalModulusSealUp$ packet must name one shared cofinal source route before any of the rows $T,D,R,L,E$ can be consumed. In particular, the rows $B,M,W$ are synchronized as the cofinal tail budget, Cauchy tail-modulus seal, and Real window budget for the same displayed route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cofinal-modulus-seal-carrier}. The source side contains exactly the rows $B,M,W$ before the StreamName, DyadicRatCore, RegSeqRat, CauchyLimitSeal, and RealUp rows are read.

Apply \autoref{thm:cofinal-modulus-seal-namecert-obligations}. Its cofinal route synchronization row states that $B,M,W$ expose one shared threshold, tail-modulus seal, and observation-window budget in the same packet.

The support rows $H,C,P,N$ transport, replay, source, and name that packet without adding another route source. Therefore any consumer of $T,D,R,L,E$ must first pass through the synchronized $B,M,W$ route.
\end{proof}

\begin{theorem}[Cofinal modulus seal window-budget exactness]
\label{thm:cofinal-modulus-seal-window-budget-exactness}
Every $\StreamNameUp$, $\DyadicRatCoreUp$, or $\RegSeqRatUp$ window read exported by an accepted $\CofinalModulusSealUp$ packet is routed through the same $\RealWindowBudgetUp$ row $W$ and $\CofinalTailBudgetUp$ row $B$.
\end{theorem}
\begin{proof}
Start with the synchronized source route of \autoref{thm:cofinal-modulus-seal-source-row-synchronization}. It fixes $B,M,W$ before any read of $T,D,R$ is public.

The StreamName row $T$ is selected by the cofinal threshold and the window budget, the DyadicRatCore row $D$ is attached to that selected window, and the RegSeqRat row $R$ is reached from the displayed tail windows. Thus the three readbacks share the same $B$ and $W$ rows.

No alternate window-budget coordinate appears in the carrier. The rows $H,C,P,N$ preserve the displayed route, so every exported window read is exact for the same RealWindowBudget and CofinalTailBudget rows.
\end{proof}

\begin{theorem}[Cofinal modulus seal completion readback boundary]
\label{thm:cofinal-modulus-seal-completion-readback-boundary}
Every completion-facing readback from an accepted $\CofinalModulusSealUp$ packet passes through $\CauchyTailModulusSealUp$, $\CauchyLimitSealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The packet does not claim Real completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:cofinal-modulus-seal-source-row-synchronization} to locate the source route and \autoref{thm:cofinal-modulus-seal-window-budget-exactness} to locate the window reads. Together they force completion-facing readback through the displayed $M,L,R,T,D,E$ rows and the synchronized source rows.

Now apply the existing Real handoff in \autoref{thm:cofinal-modulus-seal-real-handoff}. The Real-facing consumer reaches $E$ only through $B,M,W,T,D,R,L,E,H,C,P,N$.

Finally use non-escape from \autoref{thm:cofinal-modulus-seal-nonescape}. Since the carrier has no coordinate for host completeness, quotient equality, selected limits, or countable choice, the readback boundary is the finite packet rather than a Real-completeness principle.
\end{proof}

\begin{theorem}[Cofinal modulus seal cofinal route]
\label{thm:cofinal-modulus-seal-cofinal-route}
Every accepted $\CofinalModulusSealUp$ packet exposes one cofinal modulus-to-seal route
$$
B,M,W \to T,D,R,L,E
$$
through the support rows $H,C,P,N$. A public route that omits the cofinal tail budget, the Cauchy tail-modulus seal, or the Real window budget is outside the packet.
\end{theorem}
\begin{proof}
Start from the NameCert obligations. The cofinal route synchronization row ties $B,M,W$ to the same accepted packet before any completion-facing row is read.

Use the sibling boundaries in order. The cofinal tail budget supplies the shared threshold, the Cauchy tail-modulus seal binds the threshold to the modulus route, and the Real window budget exposes the selected observation window and regular handoff surface.

It remains to identify the public route. The completion-seal handoff row reads $T,D,R,L,E$ only downstream of $B,M,W$, while $H,C,P,N$ preserve the same packet. If any of $B,M,W$ is omitted, no displayed route reaches the seal side.
\end{proof}

\begin{theorem}[Cofinal modulus seal Real handoff]
\label{thm:cofinal-modulus-seal-real-handoff}
Every $\RealUp$ or completion-facing consumer of an accepted $\CofinalModulusSealUp$ packet factors through the displayed rows
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
The handoff exposes the $\RealUp$ seal only after the $\CofinalTailBudgetUp$, $\CauchyTailModulusSealUp$, $\RealWindowBudgetUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\CauchyLimitSealUp$ rows have been read on the same route.
\end{theorem}
\begin{proof}
Project the carrier to the Real-facing rows. The only RealUp coordinate is $E$, and it appears after the StreamName window $T$, dyadic ledger $D$, RegSeqRat handoff $R$, and Cauchy-limit seal $L$.

Apply \autoref{thm:cofinal-modulus-seal-cofinal-route}. That theorem places $T,D,R,L,E$ downstream of the synchronized source rows $B,M,W$, so no Real-facing consumer can reach $E$ from a detached window, a private modulus, or an independent limit seal.

Finally read the support rows. Transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ preserve exactly the same route. Thus the Real handoff is the displayed finite packet rather than a host completeness assertion.
\end{proof}

\begin{theorem}[Cofinal modulus seal non-escape]
\label{thm:cofinal-modulus-seal-nonescape}
No accepted $\CofinalModulusSealUp$ consumer can read beyond
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
In particular, the packet exports no quotient stream equality, host real equality, selected host limit, countable-choice selector, undisplayed completion seal, independent RealUp equality row, or ambient Real-completeness principle.
\end{theorem}
\begin{proof}
Use the NameCert obligations to enumerate the public surface. Carrier admission exposes only $B,M,W,L,R,T,D,E,H,C,P,N$, and the route synchronization and completion-seal handoff rows keep the consumer on those coordinates.

For StreamName, DyadicRatCore, and RegSeqRat reads, the route stops at $T,D,R$ after the cofinal source rows have been displayed. For RealUp and completion-facing reads, the route continues through $L,E$ and then through the same transport, continuation, provenance, and local naming rows.

The excluded objects require coordinates absent from the carrier. Since $H,C,P,N$ only preserve and name the displayed packet, no consumer can reinterpret the cofinal modulus seal as quotient equality, selected limit data, countable choice, independent Real equality, or ambient completeness.
\end{proof}

\begin{corollary}[Cofinal modulus seal strict obstruction]
\label{cor:cofinal-modulus-seal-strict-obstruction}
Let
$$
S=(B,M,W,L,R,T,D,E,H,C,P,N)
$$
be an accepted $\CofinalModulusSealUp$ packet. Suppose a completion-facing, $\RealUp$-facing, $\RegSeqRatUp$-facing, $\StreamNameUp$-facing, or $\DyadicRatCoreUp$-facing consumer displays a failure, refusal, separation, or countermodel row against a named converse or reuse route for $S$. Then that displayed row is a strict local obstruction: it blocks only the named route whose consumer-facing read factors through
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
It rejects every unlisted coordinate and cannot be reinterpreted as a global impossibility theorem, a host theorem, hidden external validation of the blocked route, quotient stream equality, countable choice, a selected host limit, host real equality, an undisplayed completion seal, or ambient Real completeness.
\end{corollary}
\begin{proof}
Start with the local obligation surface of \autoref{thm:cofinal-modulus-seal-namecert-obligations}. Its carrier-admission row lists exactly the displayed packet coordinates, its cofinal route synchronization row binds $B,M,W$ as the shared source route, its completion-seal handoff row places $L,R,T,D,E$ downstream of that route, its structural replay row restricts $H,C,P$ to transport, replay, and provenance over those same coordinates, and its non-escape row keeps every public consumer inside the local $\NameCert_{\CofinalModulusSealUp}$ row $N$.

Apply the completion non-escape obligation, \autoref{thm:cofinal-modulus-seal-completion-nonescape-obligation}. It says that no completion-facing consumer accepted by $\CofinalModulusSealUp$ can import quotient stream equality, countable choice, selected host limits, host real equality, or ambient Real completeness, and that the consumer boundary is the displayed route
$$
B,M,W,T,D,R,L,E,H,C,P,N.
$$
Thus every consumer-facing use of a displayed failure, refusal, separation, or countermodel row must be read as a row of this finite route. The row may obstruct the named converse or reuse route exactly where that route asks to read, replace, or bypass one of the displayed coordinates, but it has no access to any coordinate outside the route.

A stronger interpretation would require data not exported by the packet. A global impossibility theorem would require a theorem surface beyond the local $\NameCert_{\CofinalModulusSealUp}$ boundary; a host theorem would require host equality, host limits, host completeness, or a host proof channel; hidden external validation would require an off-packet certificate route; and quotient stream equality, countable choice, selected host limits, host real equality, undisplayed completion seals, and ambient Real completeness are precisely the coordinates excluded by \autoref{thm:cofinal-modulus-seal-completion-nonescape-obligation}. Since \autoref{thm:cofinal-modulus-seal-namecert-obligations} supplies only the displayed finite rows, the obstruction remains strict and local to the named converse or reuse route.
\end{proof}
