\leandef{BEDC.Derived.FunctorUp.PrefixFunctorCarrier}

\begin{theorem}[Prefix functor carrier from unary prefix]
\label{thm:prefix-functor-carrier-from-unary-prefix}
For the unary-continuation category, every unary prefix history determines a
prefix functor carrier. Its hom-carrier fields preserve and reflect prefixed
hom histories, and its composition field preserves displayed composition after
prefixing the endpoints.
\end{theorem}
\begin{proof}
Package the unary prefix witness together with the prefix hom-carrier
preservation theorem, the prefix reflection theorem, and the prefixed
composition preservation theorem.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.PrefixFunctorCarrier\_from\_unary\_prefix}

\begin{theorem}[Functor prefix hom-carrier preserves]
\label{thm:functor-prefix-hom-carrier-preserves}
For a unary prefix $p$, any category hom-carrier from $a$ to $b$ transports to
a category hom-carrier from $\mathsf{append}(p,a)$ to
$\mathsf{append}(p,b)$ with the same morphism history.
\end{theorem}
\begin{proof}
Use unary append closure on the two endpoints and place the original
continuation ledger under the common left prefix. The prefix is fixed on both
source and target, so the morphism history is read without alteration.
\end{proof}

\begin{theorem}[Functor prefix hom-carrier reflects]
\label{thm:functor-prefix-hom-carrier-reflects}
For a unary prefix $p$, any category hom-carrier from $\mathsf{append}(p,a)$ to
$\mathsf{append}(p,b)$ reflects to a category hom-carrier from $a$ to $b$ with
the same morphism history.
\end{theorem}
\begin{proof}
Read the prefixed endpoint carriers through unary append exactness and cancel
the common left prefix in the continuation ledger. The remaining continuation
is the unprefixed hom-carrier from $a$ to $b$ with the same morphism history.
\end{proof}

\begin{theorem}[Functor prefix hom-carrier identity closed]
\label{thm:functor-prefix-hom-carrier-identity-closed}
For a unary prefix $p$ and a unary object $a$, the empty morphism is a category
hom-carrier from $\mathsf{append}(p,a)$ to $\mathsf{append}(p,a)$.
\end{theorem}
\begin{proof}
Unary append closure carries the prefixed object. The category empty-identity
row then supplies the empty hom-carrier at that carried endpoint.
\end{proof}

\begin{theorem}[Functor prefix hom-carrier composition preserves]
\label{thm:functor-prefix-hom-carrier-comp-preserves}
For a unary prefix $p$, composable hom-carriers from $a$ to $b$ and from $b$ to
$c$ remain composable after prefixing all endpoints by $p$, and their
continuation composite has the same morphism history.
\end{theorem}
\begin{proof}
Apply \autoref{thm:functor-prefix-hom-carrier-preserves} to both factor
hom-carriers. The displayed continuation ledger is unchanged as a morphism
history, while the source, middle, and target endpoints are all read under the
same unary prefix.
\end{proof}

\begin{theorem}[Functor prefix hom-carrier composite hsame transport]
\label{thm:functor-prefix-hom-carrier-comp-hsame-transport}
For a unary prefix $p$, if two composable hom-carrier displays are transported
by $\hsame$-classified source, middle, target, and morphism data, then the
prefixed composite display transports by the same $\hsame$ data under
$\mathsf{append}(p,\cdot)$.
\end{theorem}
\begin{proof}
Transport the two factor hom-carriers by the category endpoint and morphism
transport rows, then apply prefix preservation to the transported factors.
Append congruence carries the source, middle, and target comparisons through
the fixed unary prefix, and continuation transport carries the composite
morphism comparison.
\end{proof}

\begin{theorem}[Prefix functor carrier composition public readback]
\label{thm:prefix-functor-carrier-comp-public-readback}
For a prefix functor carrier \(p\), if \(f\) is a hom-carrier from \(a\) to
\(b\), \(g\) is a hom-carrier from \(b\) to \(c\), and
\(\ContR(f,g,fg)\), then \(fg\) is displayed as a hom-carrier from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,c)\). Moreover, any displayed
hom-carrier between the same prefixed endpoints has morphism history
\(\HSame\) to \(fg\).
\end{theorem}
\begin{proof}
The composition-preservation field of the prefix functor carrier closes the
prefixed composite. Public readback follows by category hom-carrier morphism
determinacy at the same prefixed endpoints.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.PrefixFunctorCarrier\_comp\_public\_readback}

\begin{theorem}[Prefix functor carrier associative composition public readback]
\label{thm:prefix-functor-carrier-comp-assoc-public-readback}
For a prefix functor carrier \(p\), if \(f,g,h\) are composable
hom-carriers from \(a\) to \(b\), from \(b\) to \(c\), and from \(c\) to
\(d\), with displayed composites \(fg\), \(gh\), \(left\), and \(right\),
then \(left\) and \(right\) are hom-carriers from
\(\mathsf{append}(p,a)\) to \(\mathsf{append}(p,d)\), satisfy
\(\HSame(left,right)\), and compare by \(\HSame\) with every displayed
hom-carrier between those same prefixed endpoints.
\end{theorem}
\begin{proof}
The prefix functor carrier exposes a unary witness for the prefix, so
prefix associative composition preservation closes both bracketed composites
at the prefixed endpoints and supplies their associativity comparison.
Category hom-carrier morphism determinacy at the same prefixed endpoints
then compares each bracketed composite with any displayed carrier there.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.PrefixFunctorCarrier\_comp\_assoc\_public\_readback}

\begin{theorem}[Prefix functor carrier identity public readback]
\label{thm:prefix-functor-carrier-identity-public-readback}
For a prefix functor carrier \(p\) and a unary object \(a\), every displayed
hom-carrier from \(\mathsf{append}(p,a)\) to itself has morphism history
\(\hsame\) to \(\emp\).
\end{theorem}
\begin{proof}
The prefix carrier supplies unary closure for \(p\). Together with the unary
carrier for \(a\), this constructs the empty identity hom-carrier at the
prefixed endpoint. Category hom-carrier morphism determinacy then compares
any displayed endomorphism at the same endpoint with that empty identity.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.PrefixFunctorCarrier\_identity\_public\_readback}

\begin{theorem}[Prefix functor empty morphism source exactness]
\label{thm:functor-prefix-empty-morphism-source}
For histories $p,a,source$, the empty history is a category hom-carrier from
$source$ to $\mathsf{append}(p,a)$ exactly when $p$ and $a$ are unary and
$source$ is history-same to that prefixed target:
$$
\mathsf{CategoryHomCarrier}(source,\mathsf{append}(p,a),\emp)
\quad\Longleftrightarrow\quad
\mathsf{UnaryHistory}(p)\wedge\mathsf{UnaryHistory}(a)\wedge
\hsame(source,\mathsf{append}(p,a)).
$$
\end{theorem}
\begin{proof}
Apply category empty-identity exactness to the displayed empty morphism. The
target unary witness splits through append into unary witnesses for $p$ and
$a$, while the same exactness theorem gives the endpoint sameness. Conversely,
append closure rebuilds the target carrier, unary transport gives the source
carrier along endpoint sameness, and category empty-identity exactness
reconstructs the hom-carrier.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_empty\_morphism\_source\_iff}

\begin{theorem}[Prefix functor empty morphism endpoint exactness]
\label{thm:functor-prefix-hom-carrier-morphism-empty-endpoint-iff}
For histories $p,a,b,f$, a prefixed hom-carrier has empty morphism history
exactly when the unprefixed endpoints agree:
$$
\mathsf{CategoryHomCarrier}(\mathsf{append}(p,a),\mathsf{append}(p,b),f)
\Longrightarrow
\bigl(\HSame(f,\emp)\Longleftrightarrow\HSame(a,b)\bigr).
$$
\end{theorem}
\begin{proof}
The underlying category hom-carrier identifies empty morphisms with equality
of the prefixed endpoints. Left cancellation for generated-history append
removes the common prefix. Conversely, endpoint equality of $a$ and $b$
lifts through the shared prefix and the category endpoint theorem identifies
the morphism with $\emp$.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_morphism\_empty\_endpoint\_iff}

\begin{theorem}[Functor prefix hom-carrier composite result empty exactness]
\label{thm:functor-prefix-hom-carrier-comp-result-empty}
For histories $p,a,b,c,f,g,fg$, if $f$ is a hom-carrier from
$\mathsf{append}(p,a)$ to $\mathsf{append}(p,b)$, $g$ is a hom-carrier from
$\mathsf{append}(p,b)$ to $\mathsf{append}(p,c)$, and $\ContR(f,g,fg)$ holds,
then emptiness of the displayed composite result is equivalent to the two
factor morphisms being empty and the adjacent unprefixed endpoints agreeing:
$$
\hsame(fg,\emp)
\quad\Longleftrightarrow\quad
\hsame(f,\emp)\wedge\hsame(g,\emp)\wedge\hsame(a,b)\wedge\hsame(b,c).
$$
\end{theorem}
\begin{proof}
The forward direction transports the displayed continuation to empty result
and applies prefix empty-composite exactness. Conversely, the componentwise
empty data builds the empty composite continuation; continuation determinacy
compares that empty result with the displayed composite result $fg$.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_comp\_result\_empty\_iff}

\begin{theorem}[Prefix hom composite empty-middle inversion]
\label{thm:functor-prefix-hom-comp-empty-middle-inversion}
For histories $p,a,c,f,g,fg$, if $f$ is a hom-carrier from
$\mathsf{append}(p,a)$ to $\emp$, $g$ is a hom-carrier from $\emp$
to $\mathsf{append}(p,c)$, and $\ContR(f,g,fg)$, then
$$
\hsame(p,\emp)\wedge\hsame(a,\emp)\wedge\hsame(f,\emp)\wedge
\hsame(g,\mathsf{append}(p,c))\wedge
\mathsf{CategoryHomCarrier}(\emp,\mathsf{append}(p,c),fg)\wedge
\hsame(fg,\mathsf{append}(p,c)).
$$
\end{theorem}
\begin{proof}
Empty-target component exactness splits the left hom-carrier into emptiness of
the prefix, source tail, and morphism. Empty-source component exactness reads
the right morphism as the prefixed target. With $f=\emp$, the displayed
continuation identifies $fg$ with $g$, so $fg$ also reads back as
$\mathsf{append}(p,c)$; category empty-source exactness rebuilds the final
hom-carrier for $fg$.
\end{proof}
\leanchecked{BEDC.Derived.FunctorUp.FunctorPrefixHomCarrier\_comp\_empty\_middle\_inversion}
