\closureat{FunctorUp}{matureStr}[BEDC.Derived.FunctorUp.FunctorUp\_StdBridge]

\begin{closurestatus}{\FunctorUp}
  \constructivestory{A functor in this public construction is a certified carrier between already licensed $\CategoryUp$ packages, and the concrete bridge specializes it to the fixed-prefix endofunctor that sends a unary object $a$ to $\mathsf{append}(p,a)$ while carrying morphism tails through the corresponding endpoint-indexed hom carrier. The carrier accepts only those object and morphism maps whose images land in the codomain object and hom carriers and whose identity and composition preservation rows are witnessed under the codomain classifiers; raw maps that merely preserve unclassified composites are excluded by the finite obstruction rows. Two functor presentations classify together pointwise: their object images are compared by the target object classifier and their morphism images by the target hom classifier at the transported endpoints, so no host function equality or functor quotient is formed. The source, pattern, and ledger rows record the source and target category certificates, the object and morphism maps, identity and composition preservation, classifier-replacement stability, and the composite functor ledgers used for identity, unit, and associativity laws. The five name-certificate obligations follow from inhabited fixed-prefix data, pointwise reflexivity, symmetry, and transitivity of the category classifiers, and carrier transport supplied by the same pointwise classifier rows. A displayed functor row $h$ lies in the signature gap of a $\FunctorUp$ token $p$ when the source-domain accepts the source and target category data, the signature relation pairs the object/morphism-map package with an answer carrier and preservation ledger, and token introduction names that answer as $p$; concretely, the fixed prefix, all image objects, and all image morphisms must be the ones encoded by the token. The standard bridge reads this as the ordinary fixed-prefix endofunctor and its certified composition package, then reads back only the same $\CategoryUp$ classifier data. The chapter registers this classifier-respecting map construction under the name $\FunctorUp$; functoriality is a ledger of landing and preservation rows, not an imported functor category, host map equality, adjunction theory, or Kan-extension surface.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The public fixed-prefix $\FunctorUp$ export is closed over the carrier, certificate, public-readback, standard bridge, finite classifier-transport obstruction, split-monomorphism consumption surface, and the required $\CategoryUp$ source and target dependency.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.FunctorUp.FunctorUp\_StdBridge}
  \bridgestatus{bridgeChecked}
  \notclaimed{Full category equivalence, arbitrary external host functor spaces, adjunctions, Kan extensions, and limits-preservation theory are not closed here.}
  \upgradepath{No further upgrade -- chapter at top of formal axis.}
\end{closurestatus}
