\chapter{Project Governance and Incremental Maintenance}
\label{ch:project-governance}

This chapter governs the active development of newmath. The frozen baseline below is preserved for context; the live append-only rules apply to all future v1.5.6 / v1.6 / v2.0 increments.

This chapter explains how the multi-file project should evolve. It is included to prevent future versions from overwriting stable material while preserving a single coherent PDF.

\section{Frozen material}

A frozen module is a module that is kept for reference and not edited in place. Frozen modules may contain known limitations. A later module may supersede a statement, but the supersession is recorded explicitly.

\section{Live material}

Live material is added under new part directories, for example:
\begin{center}
\texttt{parts/hardening/}\qquad
\texttt{parts/extensions/}\qquad
\texttt{parts/formalization/}\qquad
\texttt{appendices/}
\end{center}
A live module may depend on frozen material, but it should not silently change it.

\section{Migration notes}

\begin{definition}[Migration note]
A migration note records a change in terminology, a strengthened theorem, a corrected assumption, or a new policy that supersedes an earlier statement. It must specify:
\begin{enumerate}
  \item the earlier location;
  \item the issue;
  \item the replacement statement;
  \item whether the earlier statement is deprecated, refined, or still valid under stronger assumptions.
\end{enumerate}
\end{definition}

\section{Recommended project phases}

\begin{enumerate}[label=\textbf{Phase \arabic*.}]
  \item Freeze the v10 finite kernel target as historical core.
  \item Verify the v10.1 finite proof sprint in an external formal environment.
  \item Complete the package/gap policy module.
  \item Construct explicit \(\NatUp\) and \(\AddUp\) naming certificates.
  \item Split completion-like, phase-like, and fold-like interfaces into independent modules.
\end{enumerate}

\begin{remark}
The master PDF should remain the public artifact. The source tree should remain the authoritative editable artifact.
\end{remark}
