\chapter{Roadmap for Re-deriving Mature Mathematics}
\label{ch:project-governance-roadmap}

\section{Research thesis}
\label{sec:roadmap-thesis}

Given the BEDC finite kernel
$$
b_0,b_1
\;\to\;
\Hist
\;\to\;
\msame,\hsame
\;\to\;
\Ext,\Cont
\;\to\;
\Ask,\Sig
\;\to\;
\Pkg,\Gap
\;\to\;
\NameCert,
$$
the project re-derives mature mathematical objects $N$ as licensed naming certificates
$$
\NameCert(N)
\;=\;
(\SourceSpec_N, \PatternSpec_N, \ClassifierSpec_N, \StabilityCert_N, \LedgerPolicy_N).
$$
A mature object such as $\mathbb{N}$, $\mathbb{R}$, $S^1$, a metric space, or a category is admitted only as the stable interface of a generative behaviour, never as a primitive input.

\section{Closure and verification axes}
\label{sec:roadmap-closure-and-verification-axes}

Every claim about a derived mature object is read on two independent axes. The closure axis records what the paper has reconstructed; the verification axis records the audit state of the corresponding Lean target. The discipline is recorded in \autoref{ch:closure-and-verification-discipline}.
$$
\boxed{(c, v) \in \TheoryClosure \times \FormalStatus.}
$$
The closure axis grades are $\seedClosure < \obligationClosure < \scopedClosure < \publicClosure < \bridgedClosure < \matureClosure$; the verification axis grades are $\unformalizedV < \formalTargetV < \encodedDefV < \scaffoldCheckedV < \theoremCheckedV < \auditCleanV < \axiomCleanV$, with $\bridgeCheckedV$ as the bridge-axis verification level. Neither axis determines the other.

\section{Anti-primitive principle}
\label{sec:roadmap-anti-primitive}

Mature constructs are not BEDC primitives:
$$
\boxed{\text{equality, function, } \mathbb{N}, \text{ addition, limit, } \mathbb{R}, \text{ circle, fold, set, type — none are kernel inputs.}}
$$
They are admitted only as licensed names. Any host-level $\texttt{Nat}$, $\texttt{List}$, definitional equality, $\texttt{Quot.sound}$, $\texttt{Classical.choice}$, or $\texttt{propext}$ that leaks into the BEDC public surface is a contamination, not a derivation. The Lean discipline (mathlib-free, $0$ axiom, $0$ sorry, no $\texttt{Classical}$, no $\texttt{Quot}$, no $\texttt{propext}$) is the mechanical enforcement of this principle.

\section{Layer index}
\label{sec:roadmap-layer-index}

The path from kernel to mature mathematics is layered. Every layer depends only on layers below it.

\begin{description}
  \item[\textbf{L0}] Marks: $b_0,b_1$.
  \item[\textbf{L1}] Histories: $\Hist$, $\msame$, $\hsame$.
  \item[\textbf{L2}] Generative dynamics: $\Ext$, $\Cont$.
  \item[\textbf{L3}] Asking and signature: $\Ask$, $\Sig$, $\sameSig$.
  \item[\textbf{L4}] Package relations and gaps: $\Pkg$, $\Gap$, $\ExactGlobalizeBase$.
  \item[\textbf{L5}] Naming and stability: $\NameCert$, $\StabilityCert$, $\LedgerPolicy$.
  \item[\textbf{L6}] Finite data: $\BoolUp$, $\OptionUp$, $\SumUp$, $\ProdUp$, $\ListUp$.
  \item[\textbf{L7}] Arithmetic: $\NatUp$, $\AddUp$, $\MulUp$, $\OrderUp$, $\IntUp$, $\RatUp$.
  \item[\textbf{L8}] Algebra: $\MonoidUp$, $\GroupUp$, $\AbGroupUp$, $\RingUp$, $\FieldUp$, $\ModuleUp$, $\VecSpaceUp$, $\FieldExtUp$, $\AlgClosureUp$, $\GaloisExtUp$, $\GaloisGroupUp$, $\SplittingFieldUp$, $\SeparableExtUp$, $\TranscendenceUp$, $\HopfAlgUp$, $\CharacterTheoryUp$, $\RepresentationRingUp$, $\InducedRepUp$, $\VermaModuleUp$.
  \item[\textbf{L9}] Order, logic, set, type: $\PreorderUp$, $\PosetUp$, $\LatticeUp$, $\SetLikeUp$, $\TypeLikeUp$, $\FirstOrderUp$, $\ModelTheoryUp$, $\ComputableUp$, $\LambdaCalcUp$, $\PartitionUp$, $\MatroidUp$, $\RamseyUp$, $\NetworkFlowUp$, $\MatchingUp$, $\LPDualityUp$, $\ShortestPathUp$, $\SpanningTreeUp$, $\ErrorCodeUp$, $\HashUp$, $\PublicKeyUp$, $\ZeroKnowledgeUp$.
  \item[\textbf{L10}] Topology, metric, completion, real: $\MetricUp$, $\TopologyUp$, $\CompletionUp$, $\RealUp$.
  \item[\textbf{L11}] Analysis: $\CalculusUp$, $\MeasureUp$, $\FunctionalAnalysisUp$, $\OdeUp$, $\PdeUp$, $\DynSystemUp$, $\ErgodicUp$, $\ProbSpaceUp$, $\RandomVarUp$, $\DistributionUp$, $\IndependenceUp$, $\CondExpUp$, $\MarkovChainUp$, $\MartingaleUp$, $\BrownianUp$, $\EntropyUp$, $\CStarAlgUp$, $\VonNeumannAlgUp$, $\OperatorIdealUp$, $\SpectralTheoremUp$, $\NuclearUp$, $\FactorUp$, $\QuantumStateUp$, $\ObservableUp$, $\UnitaryGroupUp$, $\DensityMatrixUp$, $\QuantumChannelUp$, $\EntanglementUp$, $\NewtonIterationUp$, $\InterpolationUp$, $\ApproximationUp$, $\FftUp$, $\QuadratureUp$, $\FisherInfoUp$, $\StatManifoldUp$, $\EstimatorUp$, $\HypothesisTestUp$, $\BayesianUp$, $\HypergeometricUp$, $\BesselUp$, $\ThetaFunctionUp$, $\ModularFormUp$, $\ClebschGordanUp$.
  \item[\textbf{L12}] Geometry, category, homology: $\CategoryUp$, $\FunctorUp$, $\NatTransUp$, $\ManifoldUp$, $\BundleUp$, $\HomologyUp$, $\CohomologyUp$, $\RiemannianMetricUp$, $\ConnectionUp$, $\CurvatureUp$, $\DiffFormUp$, $\DeRhamUp$, $\SymplecticUp$, $\ContactUp$, $\LieGroupUp$, $\LieAlgebraUp$, $\ExpMapUp$, $\AdjointRepUp$, $\RootSystemUp$, $\WeylGroupUp$, $\BilinFormUp$, $\CliffordUp$, $\SpinGroupUp$, $\PinGroupUp$, $\PreSheafUp$, $\SheafUp$, $\RingedSpaceUp$, $\SchemeUp$, $\AffineVarUp$, $\ProjectiveVarUp$, $\HomotopyUp$, $\SimplicialSetUp$, $\ModelCatUp$, $\InfCatUp$, $\DerivedCatUp$, $\AbelianCatUp$, $\DerivedFunctorUp$, $\SpectralSeqUp$, $\TriangulatedCatUp$, $\MonoidalCatUp$, $\EnrichedCatUp$, $\ToposUp$, $\TopGroupUp$, $\TopVecSpaceUp$, $\AffineSpaceUp$, $\ProjectiveSpaceUp$, $\ConvexSetUp$, $\PolytopeUp$, $\VectorBundleUp$, $\SimplicialComplexUp$, $\PersistentHomUp$, $\MapperUp$, $\KnotUp$, $\JonesPolynomialUp$, $\ThreeManifoldUp$, $\StackUp$.
  \item[\textbf{L13}] Number theory and spectra: $\PrimeUp$, $\PadicUp$, $\AdeleUp$, $\ZetaUp$, $\NumFieldUp$, $\RingOfIntegersUp$, $\IdealClassUp$, $\DirichletUnitUp$, $\DedekindUp$, $\LocalFieldUp$, $\CyclotomicUp$, $\EllipticCurveUp$, $\IwasawaUp$, $\ClassFieldUp$, $\RegulatorUp$.
  \item[\textbf{Bridges}] Cross-domain bridges (\autoref{sec:roadmap-cross-domain-bridges}): $\StoneDualityUp$, $\GelfandDualityUp$, $\PontryaginDualityUp$, $\TannakaKreinUp$, $\CurryHowardUp$, $\RiemannHilbertUp$, $\KoszulDualityUp$, $\LanglandsUp$, $\NoetherSymmetryUp$, $\GeomQuantizationUp$, $\DeformQuantizationUp$, $\ChernWeilUp$, $\AtiyahSingerUp$, $\HodgeBridgeUp$, $\MirrorSymmetryUp$.
  \item[\textbf{L14}] Mature-system bridge: standard models, mathlib bridge, conservativity reports.
\end{description}

The layer index is also the reviewer's priority order: directed development MUST advance the lowest open layer before nibbling above.

\section{L0--L5 finite kernel checked baseline}
\label{sec:roadmap-l0-l5-baseline}

The kernel proof DAG, in dependency order, is
$$
\Mark
\;\to\;
\Hist
\;\to\;
\Ext, \Cont
\;\to\;
\Ask, \Sig
\;\to\;
\sameSig
\;\to\;
\Pkg, \Gap
\;\to\;
\CompGap
\;\to\;
\NameCert.
$$
Before any derived interface is attempted, every node above must hold a checked verification target under the discipline of \autoref{sec:roadmap-closure-and-verification-axes}: $\msame$ and $\hsame$ as equivalences with no-confusion, $\Ext$ and $\Cont$ with associativity and unit laws, $\Ask$ and $\Sig$ with totality and determinism under the relevant policies, $\Pkg$ and $\Gap$ with their soundness/coverage/separation theorems, and $\NameCert$ as the universal admission rule.

\section{L4 exact globalization contract}
\label{sec:roadmap-l4-exact-globalization}

For any classification interface, exactness is recorded as a structured datum, not as natural language. The base contract is
$$
\ExactGlobalizeBase(\Pi,D)
\;=\;
\bigl(\text{coverage} \wedge \text{base soundness} \wedge \text{base completeness}\bigr),
$$
with the local classification $\iff$ as a derived corollary. Every downstream module that wants to claim ``visible packages classify histories exactly'' must cite $\ExactGlobalizeBase(\Pi,D)$, never the prose phrase.

\section{L6 finite data certificates}
\label{sec:roadmap-l6-finite-data}

For each of $\BoolUp$, $\OptionUp$, $\SumUp$, $\ProdUp$, $\ListUp$, the obligations are: a carrier predicate over $\Hist$; a classifier whose $\StabilityCert$ supplies reflexivity, symmetry, transitivity, and carrier transport; constructor and case-analysis stability; and ledger entries for whatever is hidden by the carrier predicate (tag bits, length unary, etc).

The finite-data public-object certificate scope is the boolean history $\mathsf{SemanticNameCert}$, the constructor-tagged optional-history certificate, the explicit ordered-product bridge together with its envelope certificate, the tagged sum $\mathsf{SemanticNameCert}$, and the list spine-bridge $\mathsf{SemanticNameCert}$. These scopes are the phase objects for $\BoolUp$ through $\ListUp$ when a chapter separates an envelope certificate from the public constructor interface.

\section{L7 arithmetic}
\label{sec:roadmap-l7-arithmetic}

\begin{itemize}
  \item $\NatUp$: unary repetition carrier; zero, successor, induction, recursion. The unary history $E_1$-tower is a seed, not a complete arithmetic.
  \item $\AddUp$: addition as a $\Cont$-driven operation, with associativity, commutativity, zero law.
  \item $\MulUp$: repeated addition, with distributivity, associativity, commutativity, one law.
  \item $\OrderUp$: comparison from the unary tower, with reflexivity, antisymmetry, totality, well-foundedness.
  \item $\IntUp$: signed pairs $(a,b)$ with $(a,b) \sim (c,d) \iff a+d = c+b$; ordered ring structure.
  \item $\RatUp$: certified rational histories with positive unary denominator; ordered field structure.
\end{itemize}

\section{L8 algebra}
\label{sec:roadmap-l8-algebra}

The algebra hierarchy is
$$
\MagmaUp
\;\to\;
\SemigroupUp
\;\to\;
\MonoidUp
\;\to\;
\GroupUp
\;\to\;
\AbGroupUp
\;\to\;
\RingUp
\;\to\;
\CommRingUp
\;\to\;
\FieldUp
\;\to\;
\ModuleUp
\;\to\;
\VecSpaceUp.
$$
Each layer ships a carrier, a classifier shared with the layer above, operation stability obligations, congruence laws, and a ledger of normalised expression provenance. $\LinMapUp$, $\MatrixUp$, $\PolynomialUp$ live above $\VecSpaceUp$.

The field side admits a parallel extension hierarchy: $\FieldExtUp$ packages a field embedding with the larger field as a vector space over the smaller; $\AlgClosureUp$ admits the closure under polynomial roots; $\SeparableExtUp$, $\SplittingFieldUp$, $\GaloisExtUp$, $\GaloisGroupUp$ admit normality, root-splitting, simultaneous separability and normality, and the automorphism group fixing the base field; $\TranscendenceUp$ admits the transcendence degree. $\HopfAlgUp$ admits a bialgebra with antipode, sitting above $\RingUp$ and $\TensorProductUp$.

\section{L9 order, logic, set-like, type-like}
\label{sec:roadmap-l9-order-logic-set-type}

$\PreorderUp$, $\PosetUp$, $\TotalOrderUp$, $\LatticeUp$ are licensed by stable comparison behaviour. $\SetLikeUp$ is licensed by classifier-based membership: the membership predicate is generated, never assumed; subset is implication of membership; comprehension is restricted to certified families; extensionality is a certificate field, not a primitive. $\TypeLikeUp$ is the corresponding carrier-plus-classifier-plus-transport interface.

The logic side admits a first-order signature, formula carrier, and deduction calculus through $\FirstOrderUp$, with the soundness and completeness data; $\ModelTheoryUp$ admits a structure for that signature with satisfaction and elementary equivalence. The computability side admits $\ComputableUp$ as Turing-machine-step-bounded partial functions and $\LambdaCalcUp$ as the inductive carrier of $\lambda$-terms with $\beta$-reduction and $\alpha$-equivalence. The combinatorial side admits $\PartitionUp$ as Young-diagram-presented integer partitions, $\MatroidUp$ as exchange-axiom independent-set families, and $\RamseyUp$ as the monochromatic-subset bound under finite colouring.

\section{L10 topology, metric, completion, real}
\label{sec:roadmap-l10-topology-metric-completion-real}

This layer crosses the line between finite-history objects and countable-name objects. The architectural cost has to be paid up front.

\subsection*{Architectural gate: countable names}
\label{sec:roadmap-l10-stream-name}

A finite history $\Hist$ cannot itself encode an infinite object. To license $\RealUp$ and onward, the project admits \emph{certified countable names}: a name is a function whose finite observations are individually certified by an existing carrier, and whose stability is the pointwise classifier of those observations. Concretely, the milestone $\StreamNameUp$ supplies a carrier of the form
$$
\StreamCarrier_X(s) \;\equiv\; \forall n,\; \UnaryHistory(n) \to X{\text{Carrier}}(s\,n),
$$
with the pointwise classifier
$$
\StreamSame_X(s,t) \;\equiv\; \forall n,\; \UnaryHistory(n) \to X{\text{Same}}(s\,n,\,t\,n),
$$
and stability obligations: pointwise reflexivity / symmetry / transitivity inherited from the point certificate, carrier transport along the pointwise classifier, reindexing stability under $\hsame$, mapped-stream stability, and an inhabited stream from a constant certified point.

This is not optional. Without $\StreamNameUp$, the L10 layer is not feasible under the discipline.

\subsection*{Construction order}
\label{sec:roadmap-l10-construction-order}

The interior of L10 is itself a sub-roadmap. The construction order, with each step depending only on earlier steps, is

\begin{enumerate}
  \item $\DyadicRatCore$: dyadic rationals over $\IntUp$ and the unary exponent tower. Carrier: signed mantissa with unary exponent. Classifier: dyadic equality by common-exponent scaling, encoded as a predicate, not via $\Quot$. Obligations: arithmetic stability, monotone $2^{-n}$ radii, distance and absolute value stability. Estimated $25$--$40$ rounds.
  \item $\StreamNameUp$ (architectural gate above). Estimated $8$--$12$ rounds.
  \item $\RegSeqRat$: Bishop-style regular Cauchy sequences over dyadic rationals. Carrier: a stream over $\DyadicRatCore$ satisfying $|x_n - x_m| \le 2^{-n} + 2^{-m}$. Classifier: regular-sequence closeness via dyadic $\varepsilon$-tolerance. Obligations: regularity carrier, refl/symm/trans by $\varepsilon$ halving, shift and tail stability. Estimated $30$--$45$ rounds.
  \item $\RealUp$: real names sealed as $\RegSeqRat$ data with classifier closeness. Constant dyadic embedding respects classifier. No claim of completeness yet. Estimated $20$--$35$ rounds.
  \item $\RealAlgOrder$: addition, negation, multiplication, absolute value, nonnegative order, strict apartness on $\RealUp$. Order is constructive: prefer apartness over classical trichotomy. Estimated $35$--$60$ rounds.
  \item $\MetricSpaceUp$: certified metric structure over a parameterised point carrier, with a $\RealUp$-valued distance, classifier-based identity of indiscernibles, symmetry, triangle inequality. Estimated $12$--$20$ rounds.
  \item $\SOneUp$: $S^1$ as the certified subspace of $\RealUp \times \RealUp$ with $x^2 + y^2 \approx 1$ under $\RealClassifier$. No angle parametrisation yet. Estimated $20$--$35$ rounds.
  \item $\TotallyBoundedUp$: total boundedness as explicit dyadic $\varepsilon$-net data, witnessed via $\mathsf{ProbeBundle}$ induction. Not open-cover compactness. Estimated $18$--$30$ rounds.
  \item $\CompleteMetricUp$: metric completeness as convergence of regular Cauchy point names; uniqueness of limits conditional on separatedness. Estimated $25$--$40$ rounds.
  \item $\CompactMetricUp$: $\CompactMetricCarrier(X) \equiv \MetricSpaceCarrier(X) \wedge \CompleteCarrier(X) \wedge \TotallyBoundedCarrier(X)$. Compact $[0,1]$ and compact $S^1$ are exhibited via explicit dyadic nets. Estimated $12$--$20$ rounds for the definition; $40+$ for product / subspace theorems.
  \item $\ContinuousMapUp$: uniformly continuous maps with explicit modulus, classifier-based equality on source carrier points, identity and composition stability. Estimated $20$--$35$ rounds.
\end{enumerate}

The L10 sub-roadmap totals roughly $250$--$400$ rounds. The honest first reportable target is finishing items 1--4, which produces the project's first fully licensed infinite mature-object name: $\RealUp$.

\subsection*{Constructive constraints to honour}
\label{sec:roadmap-l10-constructive-constraints}

The standard equivalences below are not generally derivable in this discipline and must not be claimed as such:
\begin{itemize}
  \item Dedekind-cut construction of $\mathbb{R}$.
  \item Open-cover compactness as a general theorem on $\CompactMetricUp$.
  \item Sequential compactness without choice-like data.
  \item Heine-Borel as a general result on subsets of $\RealUp$.
  \item Trichotomy of constructive reals.
  \item Quotient-by-equivalence-class as a primitive.
\end{itemize}
Workable substitutes are the constructive analogues: located reals, total boundedness with explicit nets, separated metric spaces with explicit completion data, apartness in place of classical trichotomy, and classifier predicates in place of quotient types.

\section{L10 topology continued and L11 analysis}
\label{sec:roadmap-l11-analysis}

$\TopologyUp$ is licensed by an open-set classifier predicate, neighbourhood interface, finite intersection and arbitrary union closure, continuous maps stable under the classifier, product and quotient topologies via the existing product / classifier mechanisms. $\CompletionUp$ generalises the regular-Cauchy completion mechanism beyond $\RatUp$ to any metric carrier, with operation descent recorded in the ledger.

$\CalculusUp$ admits derivative as a stable local linear approximation, integral via completion of finite sums or via a measure-based interface, with the fundamental theorem deferred until the measure interface is stable. $\MeasureUp$ admits stable event algebra, $\sigma$-stability, integration, conditional expectation, $L^p$ spaces. $\FunctionalAnalysisUp$ admits normed and inner-product spaces, Banach and Hilbert completion, bounded and compact operators, spectrum, with the spectral theorem as a major target.

The differential side admits $\OdeUp$ as systems $\dot x = F(t,x)$ with local existence and uniqueness on Lipschitz vector fields, $\PdeUp$ as classified relations among partial derivatives on a manifold carrier, $\DynSystemUp$ as one-parameter flows on phase-space carriers, and $\ErgodicUp$ as measure-preserving transformations with their invariant decomposition. The probability side admits $\ProbSpaceUp$ as a measure space of total mass $1$, $\RandomVarUp$ as a measurable function from a probability space, $\DistributionUp$ as the pushforward measure on the target, $\IndependenceUp$ as joint-distribution factorisation, $\CondExpUp$ as the $L^2$ projection onto a sub-$\sigma$-algebra, $\MarkovChainUp$ and $\MartingaleUp$ as adapted sequences with the Markov / martingale increment law, $\BrownianUp$ as the continuous-time Gaussian-increment process with continuous sample paths, and $\EntropyUp$ as the Shannon and differential entropies.

\section{L12 categories, geometry, homology}
\label{sec:roadmap-l12-categories-geometry-homology}

\subsection*{Categories}

$\CategoryUp$ admits objects as certified carriers, morphisms as records over $\ContinuousMapUp$ or other certified maps, identity and composition stability, associativity and unit laws up to morphism classifier. Object equality is never extensional: subcategory inclusion is data, isomorphism is a record. $\FunctorUp$ and $\NatTransUp$ extend the same pattern.

\subsection*{Differential geometry}

$\ManifoldUp$ admits charts, atlas compatibility, gluing. $\BundleUp$ admits local trivialisation, transition functions, cocycle conditions. $\RiemannianMetricUp$ admits a smooth field of inner-product certificates on tangent fibres. $\ConnectionUp$ admits a covariant derivative on a fibre bundle, with linearity in the section argument and Leibniz against scalar functions. $\CurvatureUp$ admits the antisymmetric bracket of a connection, with Bianchi identities and tensorial behaviour under section change. $\DiffFormUp$ admits antisymmetric multilinear maps on the tangent bundle, with wedge product. $\DeRhamUp$ admits the exterior-derivative chain complex with $d^2 = 0$. $\SymplecticUp$ admits a closed nondegenerate $2$-form on an even-dimensional manifold. $\ContactUp$ admits a maximally nonintegrable hyperplane field on an odd-dimensional manifold.

\subsection*{Lie theory}

$\LieGroupUp$ admits a group whose underlying carrier is a manifold and whose multiplication and inverse are constructively smooth. $\LieAlgebraUp$ admits a vector space with antisymmetric bracket satisfying Jacobi. $\ExpMapUp$ admits the canonical $\mathfrak{g} \to G$ map for a connected Lie-group carrier. $\AdjointRepUp$ admits the conjugation action $\mathrm{Ad}$ together with its differential $\mathrm{ad}$. $\RootSystemUp$ admits a finite reflection-closed set of nonzero vectors with integer Cartan pairings. $\WeylGroupUp$ admits the finite reflection group generated by simple roots.

\subsection*{Clifford and geometric algebra}

$\BilinFormUp$ admits a bilinear pairing on a module carrier with symmetry, antisymmetry, and nondegeneracy classifiers. $\CliffordUp$ admits the universal associative algebra modulo $v \cdot v = q(v)$. $\SpinGroupUp$ admits the connected double cover of the orthogonal group as a subgroup of the Clifford-algebra units. $\PinGroupUp$ admits the double cover of the full orthogonal group, extending Spin by a reflection generator.

\subsection*{Algebraic geometry}

$\PreSheafUp$ admits a contravariant functor from the open-sets category to a target category, with restriction maps respecting composition and identity. $\SheafUp$ admits a presheaf satisfying locality and gluing over open covers. $\RingedSpaceUp$ admits a topological carrier with a sheaf of commutative rings whose stalks form local rings. $\SchemeUp$ admits a locally ringed space covered by spectra of commutative rings. $\AffineVarUp$ admits the zero-locus of a finite system of polynomial equations in affine $n$-space. $\ProjectiveVarUp$ admits the zero-locus of a homogeneous polynomial ideal in projective $n$-space.

\subsection*{Homology and homotopy}

$\HomologyUp$ admits chain complex, kernel/cokernel, exact sequence, derived functor. $\CohomologyUp$ admits the dual cochain complex with cup product. $\HomotopyUp$ admits the equivalence-of-paths relation between continuous maps under continuous deformation. $\SimplicialSetUp$ admits a contravariant functor from the simplex category $\Delta$ to certified sets, with face and degeneracy operators satisfying the simplicial identities. $\ModelCatUp$ admits a category with three distinguished classes of morphisms (cofibrations, fibrations, weak equivalences) satisfying lifting and factorisation axioms. $\InfCatUp$ admits a simplicial-set carrier satisfying inner-horn lifting (a quasicategory). $\DerivedCatUp$ admits the localisation of a chain-complex category at quasi-isomorphisms.

\section{L13 number theory and spectra}
\label{sec:roadmap-l13-number-theory-spectra}

$\PrimeUp$ admits divisibility, irreducibility, primality, gcd, Euclidean algorithm, unique factorisation. $\PadicUp$ admits the $p$-adic valuation, $p$-adic metric, completion to a local field. $\AdeleUp$ admits the local-global product formula, adele-like interface. $\ZetaUp$ admits dynamical zeta, Euler product, Dirichlet series, with analytic continuation deferred to a stable analysis substrate. Riemann-hypothesis-shaped statements remain theorem targets, never naming-seed assertions.

The deeper number-theoretic side admits $\NumFieldUp$ as a finite field extension of $\RatUp$; $\RingOfIntegersUp$ as the integral closure of $\IntUp$ in such a number field; $\IdealClassUp$ as the quotient group of fractional ideals modulo principals over a Dedekind domain; $\DirichletUnitUp$ as the finitely generated abelian unit-group structure with Dirichlet rank; $\DedekindUp$ as the integrally closed Noetherian domain with maximal nonzero primes; $\LocalFieldUp$ as a complete discretely valued field with finite residue field; $\CyclotomicUp$ as the splitting field of $X^n - 1$; and $\EllipticCurveUp$ as a smooth projective genus-one curve with chosen base point.

\section{L14 conservative bridge to mature systems}
\label{sec:roadmap-l14-bridge}

For every certified mature object $N$ a bidirectional bridge is established:
$$
\BEDC(N) \;\longrightarrow\; \mathrm{Std}(N),
\qquad
\mathrm{Std}(N) \;\longrightarrow\; \BEDC(N).
$$
The bridge proves at minimum: BEDC certificates interpret as standard objects; standard objects encode as BEDC certificates; basic theorems hold on both sides; no host primitive enters the BEDC public surface. The bridge to Lean / mathlib in particular records mapping tables, theorem correspondences, proof dependency maps, unsupported features, and a contamination audit.

\section{Cross-domain bridges via the unified kernel}
\label{sec:roadmap-cross-domain-bridges}

Because every certificate in this project is read off the same finite kernel
$$\Mark \to \Hist \to \Ext, \Cont \to \Ask, \Sig \to \Pkg, \Gap \to \NameCert,$$
two domains that traditionally appear unrelated meet inside a common classifier substrate as soon as both are licensed. A bridge is then itself a naming certificate: the source carrier is one of the two domains, the pattern is the other, and the classifier is the shared identification. Bridges are not metatheorems; they live inside the same framework as their endpoints, with $\TheoryClosure \times \FormalStatus$ status tracked on both axes.

The currently scoped bridges are:
\begin{description}
  \item[\textbf{Order $\leftrightarrow$ Topology}] $\StoneDualityUp$ identifies Boolean algebras with Stone spaces.
  \item[\textbf{Operator algebra $\leftrightarrow$ Topology}] $\GelfandDualityUp$ identifies commutative C*-algebras with compact Hausdorff spaces.
  \item[\textbf{Topological group $\leftrightarrow$ Abelian group}] $\PontryaginDualityUp$ pairs LCA groups with their character duals.
  \item[\textbf{Lie group $\leftrightarrow$ Tensor category}] $\TannakaKreinUp$ recovers a compact group from its representation category.
  \item[\textbf{Logic $\leftrightarrow$ Computation}] $\CurryHowardUp$ identifies propositions with types and proofs with programs.
  \item[\textbf{Differential $\leftrightarrow$ Topological}] $\RiemannHilbertUp$ identifies regular holonomic D-modules with perverse sheaves.
  \item[\textbf{Algebra $\leftrightarrow$ Homological}] $\KoszulDualityUp$ identifies graded algebras with their Koszul duals.
  \item[\textbf{Galois $\leftrightarrow$ Automorphic}] $\LanglandsUp$ matches Galois representations to automorphic representations through L-factors.
  \item[\textbf{Symmetry $\leftrightarrow$ Conservation}] $\NoetherSymmetryUp$ pairs continuous Lagrangian symmetries with conserved currents.
  \item[\textbf{Symplectic $\leftrightarrow$ Hilbert}] $\GeomQuantizationUp$ assigns a Hilbert space to a symplectic manifold via prequantum data and polarisation.
  \item[\textbf{Poisson $\leftrightarrow$ Noncommutative}] $\DeformQuantizationUp$ pairs a Poisson manifold with a formal star product whose first-order term is the bracket.
  \item[\textbf{Differential $\leftrightarrow$ Topological invariant}] $\ChernWeilUp$ expresses characteristic cohomology classes through curvature forms.
  \item[\textbf{Spectral $\leftrightarrow$ Topological}] $\AtiyahSingerUp$ matches the analytic index of an elliptic operator with a topological index in cohomology.
  \item[\textbf{Complex-analytic $\leftrightarrow$ Topological}] $\HodgeBridgeUp$ decomposes de Rham cohomology of a Kähler manifold into harmonic $(p,q)$-forms.
  \item[\textbf{Symplectic $\leftrightarrow$ Complex-algebraic}] $\MirrorSymmetryUp$ pairs the A-model of one Calabi-Yau with the B-model of its mirror.
\end{description}
The bridge inventory is open: any two licensed naming certificates whose carriers identify under a stable classifier yield a new bridge namecert, and the unified-kernel discipline is what makes such bridges first-class citizens of the framework rather than miracles.

\section{Per-object research template}
\label{sec:roadmap-per-object-template}

Every milestone is filed under the same ten-field template:
\begin{enumerate}
  \item \textbf{Traditional target}: how $N$ appears in mature mathematics.
  \item \textbf{BEDC source}: which already-licensed BEDC objects generate it.
  \item \textbf{Carrier choice}: predicate (or stream) over the source.
  \item \textbf{Classifier choice}: equivalence relation, never $\Quot$.
  \item \textbf{Stability obligations}: refl/symm/trans, carrier transport, operation congruence, descent, completion / seal where relevant.
  \item \textbf{Ledger}: what is hidden, projected, compressed, completed.
  \item \textbf{Core theorem list}: the minimum set that must hold.
  \item \textbf{Exactness predicate}: coverage, soundness, completeness, classification $\iff$.
  \item \textbf{Standard bridge}: the conservative back-and-forth to the mature reference.
  \item \textbf{Status}: a pair $(c, v)$ where $c \in \TheoryClosure$ is the closure axis grade and $v \in \FormalStatus$ is the verification axis grade.
\end{enumerate}

\section{Near-term phases}
\label{sec:roadmap-near-term-phases}

The near-term path is a small number of phase bundles. Each phase has a specific exit criterion and is the only sanctioned advancement direction during its tenure.

\begin{description}
  \item[\textbf{Phase Kernel-Checked Baseline}] L0--L5, including $\msame$, $\hsame$, $\Ext$, $\Cont$, $\Sig$, $\Gap$, $\NameCert$, $\ExactGlobalizeBase$. Exit criterion:
    \begin{itemize}
      \item Closure axis: kernel proof obligations are supplied through the finite-kernel proof DAG ending at $\NameCert$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ for every cited kernel target $N$.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Finite Data}] L6, $\BoolUp$ through $\ListUp$, with the ten-field template completed for each. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\BoolUp, \OptionUp, \SumUp, \ProdUp, \ListUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Full Nat Arithmetic}] L7, $\NatUp$ through $\RatUp$, with induction, recursion, ordered-ring and ordered-field structure. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\NatUp, \AddUp, \MulUp, \OrderUp, \IntUp, \RatUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Algebra Hierarchy}] L8 up to $\FieldUp$. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\MonoidUp, \GroupUp, \AbGroupUp, \RingUp, \CommRingUp, \FieldUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Real and Completion}] L10 items 1--4 of section~\ref{sec:roadmap-l10-construction-order}: $\DyadicRatCore$, $\StreamNameUp$, $\RegSeqRat$, $\RealUp$. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\DyadicRatCore, \StreamNameUp, \RegSeqRat, \RealUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Real Algebra and Geometry}] L10 items 5--7: $\RealAlgOrder$, $\MetricSpaceUp$, $\SOneUp$. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\RealAlgOrder, \MetricSpaceUp, \SOneUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Compact and Continuous}] L10 items 8--11: $\TotallyBoundedUp$, $\CompleteMetricUp$, $\CompactMetricUp$, $\ContinuousMapUp$. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\TotallyBoundedUp, \CompleteMetricUp, \CompactMetricUp, \ContinuousMapUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Linear Algebra and Analysis Seed}] L8 vector-space layer plus L11 calculus seed: $\VecSpaceUp$, $\LinMapUp$, $\MatrixUp$, $\NormUp$, $\HilbertUp$. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every $N$ in $\{\VecSpaceUp, \LinMapUp, \MatrixUp, \NormUp, \HilbertUp\}$.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited Lean targets.
      \item Bridge status: pending.
    \end{itemize}
  \item[\textbf{Phase Category and Bridge}] L12 $\CategoryUp$ and L14 bridge for already-checked objects. Exit criterion:
    \begin{itemize}
      \item Closure axis: $\TheoryGate(N, \scopedClosure)$ for every phase object, with $\bridgedClosure$ only for objects whose standard bridge is explicitly supplied.
      \item Verification axis: $\FormalStatus(N, \auditCleanV)$ on the cited BEDC Lean targets and $\FormalStatus(N, \bridgeCheckedV)$ on bridge targets where claimed.
      \item Bridge status: supplied for the named bridge deliverables and pending elsewhere.
    \end{itemize}
\end{description}

The reviewer pipeline picks targets in service of the current open phase. Targets that advance a later phase while the current phase is open are deferred. The roadmap is maintained in place when a phase exits, without version annotations.

\section{Claims explicitly off the table}
\label{sec:roadmap-off-the-table}

The discipline of this manuscript is two-axis. The following readings are refused:
\begin{enumerate}
  \item BEDC has re-derived all of mature mathematics.
  \item $\RealUp$ is complete.
  \item $\SOneUp$ is complete.
  \item $\FoldUp$ is complete.
  \item $\NatUp$ at $\scopedClosure$ equals full natural-number theory.
  \item $\AddUp$ at $\scopedClosure$ equals full addition.
  \item Paper certificates equal machine-checked certificates.
  \item Lean scaffolds equal verified implementations.
  \item External standard models replace BEDC internal proof obligations.
  \item Host equality, host $\mathsf{Nat}$, or host functions are part of the BEDC public surface.
  \item Machine verification is required for theoretical closure.
  \item Without $\theoremCheckedV$ no closure grade above $\seedClosure$ may be claimed.
  \item A checked theorem-shape scaffold closes the corresponding object theory.
  \item A scoped certificate closure is a full traditional-object reconstruction.
  \item A bridge is closed merely because the BEDC-side certificate is checked.
\end{enumerate}

The discipline of this roadmap is condensed in one line:
$$
\boxed{\text{a derivation does not assume the mature object exists; it proves a name has earned the right to be used.}}
$$
