\begin{theorem}[DyadicApproximation DyadicRatCore dependency route]
\label{thm:dyadic-approximation-dyadicratcore-dependency-route}
Every accepted $\DyadicApproximationUp$ finite packet consumes the $\DyadicRatCoreUp$ signed-exponent row, scale-window row, and finite-tail row of \autoref{ch:concrete-instances-dyadicratcore-namecert} before it may hand a mesh, validated enclosure, or terminal seal to $\RealUp$. The route passes through the local finite-packet readback and exactness surfaces of \autoref{thm:dyadicapproximation-finite-packet-readback-exhaustion}, \autoref{thm:dyadicapproximation-refined-finite-packet-readback-determinacy}, \autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback}, and \autoref{thm:dyadicapproximation-finite-mesh-enclosure-exactness}; it exports no host rational equality, quotient stream, selected limit, or ambient completion object.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_dyadicratcore\_dependency\_route}
\begin{proof}
Start with the finite-packet readback exhaustion theorem. It places every accepted DyadicApproximation consumer read on the displayed precision, $\DyadicRatCoreUp$ endpoint window, stream window, regular-rational readback, $\RealUp$ seal, refinement, overlap, transport, continuation, package, and local certificate rows.

Use the refined finite-packet determinacy and terminal finite-packet Real readback theorems next. These keep the transported precision, endpoint window, validated enclosure, stream window, regular-rational readback, and $\RealUp$ seal on one finite packet surface.

Finally apply the finite mesh-enclosure exactness surface. The mesh or enclosure handed to $\RealUp$ is exact only after the DyadicRatCore signed exponent, scale window, and finite tail have been consumed through the cited sibling chapter. Therefore the dependency route is a substantive DyadicRatCore route rather than a decorative cross-reference.
\end{proof}
