\begin{theorem}[DyadicApproximation finite packet readback exhaustion]
\label{thm:dyadicapproximation-finite-packet-readback-exhaustion}
Let $A=(n,d,w,l,p)$ be an accepted $\DyadicApproximationUp$ finite packet, and let
$C$ be a finite-packet consumer whose reads of $A$ are routed through the public
finite-window export, the terminal overlap chain, the overlap refinement normal
form, and the $\DyadicMeshUp/\ValidatedNumericsUp$ consumer normal form.

Then the readback surface seen by $C$ is exactly the displayed precision row
$n$, the $\DyadicRatCoreUp$ endpoint window, the finite $\RegSeqRatUp$ readback
window, the $\RealUp$ seal token, the refinement ledger, the overlap route, the
visible $\hsame$ transports, the visible $\Cont$ routes, the $\mathsf{Pkg}$
provenance rows, the local $\NameCert_{\DyadicApproximationUp}$ rows, and the
validated enclosure handoff carried by the displayed
$\DyadicMeshUp/\ValidatedNumericsUp$ consumer boundary.

The readback surface has no coordinate for a completed real, infinite mesh,
solver state, host interval object, host equality, selected representative,
trichotomy row, or choice data.
\end{theorem}
\begin{proof}
First project the accepted packet through
\autoref{thm:dyadicapproximation-public-finite-window-export}. The public rows
are the displayed precision, dyadic endpoint, stream window, regular-rational
readback, real-seal ledger, visible transport and continuation routes, package
provenance, and local certificate data.

Next stabilize the overlap access. Apply
\autoref{thm:dyadicapproximation-terminal-window-idempotence} to the terminal
read and then apply
\autoref{thm:dyadicapproximation-overlap-refinement-chain-normal-form} to the
compatible overlap refinement chain. These two results identify the terminal
overlap route with the same finite packet rows and leave no second endpoint,
precision row, provenance row, or seal coordinate.

Now pass to the downstream consumer. By
\autoref{thm:dyadicapproximation-dyadicmesh-validatednumerics-consumer-normal-form},
the $\DyadicMeshUp$ cell and the $\ValidatedNumericsUp$ enclosure read only the
displayed containment row, mesh level and cell-index rows, endpoint window,
enclosure handoff, containment routes, package provenance, and local certificate
rows attached to the same dyadic packet.

Coordinate exhaustion finishes the claim. Every row available to $C$ appears in
one of the three projected surfaces just listed, and the listed surfaces have no
carrier field or certificate row for a completed real, infinite mesh, solver
state, host interval object, host equality, selected representative, trichotomy
row, or choice data.
\end{proof}
