\begin{theorem}[DyadicApproximation terminal selector determinacy]
\label{thm:dyadicapproximation-finite-packet-terminal-selector-determinacy}
Let $A$ and $A'$ be accepted terminal $\DyadicApproximationUp$ finite packets.
Suppose their terminal rows are identified by displayed $\hsame$ comparisons,
they expose the same $\RationalIntervalUp$ window, the same $\RegSeqRatUp$
readback, and the same $\RealUp$ seal-facing route through visible $\Cont$,
$\Pkg$, and local $\NameCert_{\DyadicApproximationUp}$ provenance.

Then the terminal selector reads of $A$ and $A'$ classify together. Equivalently,
after the terminal finite-window surface is fixed, the selector cannot depend
on an unlogged mesh endpoint or on any endpoint coordinate outside the accepted
finite packets.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_finite\_packet\_terminal\_selector\_determinacy}
\begin{proof}
First normalize both terminal reads. Apply
\autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback} to each
accepted packet. The terminal selector is thereby expressed through the
terminal precision row, transported endpoint, $\RationalIntervalUp$ window,
$\RegSeqRatUp$ readback, $\RealUp$ seal ledger, visible transports,
continuation routes, package provenance, and local certificate rows.

Next place the two packets on a common enclosure surface. Apply
\autoref{thm:dyadicapproximation-common-refinement-enclosure-handoff}. The
shared rational interval, regular-rational readback, and real seal route are
therefore read from one finite $\RealUp$ boundary surface.

Now commute the refinement with the seal route. Apply
\autoref{thm:dyadicapproximation-refinement-seal-commutation}. This shows that
reading the terminal selector before the seal and reading through the common
refinement before the seal expose the same finite coordinates.

Finally use
\autoref{thm:dyadicapproximation-shared-real-boundary-determinacy}. Since the
hypotheses identify the terminal rows, interval window, regular readback, real
seal route, transports, continuations, and provenance, every permitted consumer
route reads the same boundary. No cited surface contains an unlogged mesh
endpoint, so the terminal selector has no remaining coordinate on which a
different classification could depend.
\end{proof}
