\begin{theorem}[DyadicApproximation finite-packet StreamName Real-seal factorization]
\label{thm:dyadicapproximation-finite-packet-streamname-real-seal-factorization}
Let $T$ be an accepted terminal $\DyadicApproximationUp$ finite packet and let
$D$ be an accepted $\RealDiagonalCompletionUp$ packet. Suppose the displayed
terminal route for $T$ contains its terminal precision, dyadic endpoint,
scheduled $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealUp$ seal
ledger, visible $\hsame$ transports, visible $\Cont$ routes, $\Pkg$
provenance, local $\NameCert_{\DyadicApproximationUp}$ row, and the
diagonal-completion selector rows consumed by $D$.

Then the route that first applies the StreamName $\RealUp$ seal factorization
diamond and the route that first applies the $\DyadicApproximationUp$ terminal
diagonal-completion handoff expose the same finite $\mathsf{BHist}$ surface.
That surface is exactly the StreamName finite-window row, $\RegSeqRatUp$
readback, dyadic endpoint rows, terminal precision row, $\RealUp$ seal token,
diagonal selector row, transport rows, continuation rows, package provenance,
and local $\NameCert_{\DyadicApproximationUp}$ provenance.

The surface assertion is only this finite packet factorization. It does not
assert completed real equality, quotient streams, selected host limits, solver
correctness, metric completeness, or any standard bridge.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_streamname\_real\_seal\_factorization\_certificate}
\begin{proof}
First normalize the dyadic terminal route. Apply
\autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback} to the
accepted terminal packet $T$. This reads the terminal consumer through the
displayed terminal precision, dyadic endpoint, scheduled $\StreamNameUp$
window, $\RegSeqRatUp$ readback, $\RealUp$ seal row, transport rows,
continuation rows, package provenance, and local dyadic certificate row.

Next normalize the refinement and seal route. Apply
\autoref{thm:dyadicapproximation-finite-packet-real-seal-stability} to place
the terminal readback and the $\RealUp$ seal on one finite refinement surface.
Apply
\autoref{thm:dyadicapproximation-terminal-seal-common-refinement-pullback} to
pull that seal surface back to the visible terminal boundary.

Now identify the StreamName source tuple. Apply
\autoref{thm:streamname-real-seal-factorization-diamond} to the scheduled
$\StreamNameUp$ finite window and its displayed prefix refinement. The
diamond leaves exactly the StreamName finite-window row, accepted
$\RegSeqRatUp$ source row, dyadic endpoint rows, continuation ledger,
endpoint transports, and provenance rows visible to the $\RealUp$ seal.

Finally identify the diagonal-completion consumer rows. Apply
\autoref{thm:dyadicapproximation-terminal-diagonal-completion-handoff} to the
same terminal packet and diagonal-completion packet. The handoff contributes
the diagonal selector row and confirms that the terminal precision, endpoint,
scheduled window, regular-rational readback, seal ledger, transports,
continuations, package rows, and local certificate row are the rows consumed by
the diagonal route.

The two normal forms therefore list the same finite coordinates. Repacking
those coordinates gives one $\mathsf{BHist}$ surface containing exactly the
StreamName finite-window row, $\RegSeqRatUp$ readback, dyadic endpoint rows,
terminal precision row, $\RealUp$ seal token, diagonal selector row,
transport rows, continuation rows, package provenance, and local
$\NameCert_{\DyadicApproximationUp}$ provenance. None of the cited finite
surface theorems supplies a coordinate for completed real equality, quotient
streams, selected host limits, solver correctness, metric completeness, or a
standard bridge.
\end{proof}
