\begin{theorem}[DyadicApproximation mesh validated Real boundary]
\label{thm:dyadicapproximation-mesh-validated-real-boundary}
Let $A=(n,d,w,l,p)$ be an accepted $\DyadicApproximationUp$ packet. Let
$M=(\ell,J,I,E,H,C,P,N)$ be an accepted $\DyadicMeshUp$ cell whose
$\RationalIntervalUp$ cell $I$ contains the transported dyadic endpoint $d$ at
the displayed precision $n$. Let
$V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p',n')$ be an accepted
$\ValidatedNumericsUp$ enclosure over the same rational-interval cell and the
same containment ledger.

Suppose the displayed precision row, dyadic endpoint row,
rational-interval cell, containment ledger, regular-rational window, mesh level
and index, real-readback token, visible $\hsame$ transports, visible $\Cont$
routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows are shared by the
three accepted packets. Then the DyadicApproximation terminal finite-window
route, the DyadicMesh cell-containment route, and the ValidatedNumerics
real-readback route expose exactly one finite $\RegSeqRatUp/\RealUp$ consumer
surface.

The shared surface is precisely the precision row, endpoint row,
rational-interval cell, mesh level and index, regular-rational window,
validated containment ledger, real readback token, visible $\hsame$ transports,
visible $\Cont$ routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows.
It exports no solver correctness, floating-point semantics, host real equality,
quotient reals, or classical completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_mesh\_validated\_real\_boundary}
\begin{proof}
First expose the DyadicApproximation terminal route. Apply
\autoref{thm:dyadicapproximation-finite-packet-readback-exhaustion} to account
for every public read of $A$, and apply
\autoref{thm:dyadicapproximation-terminal-validated-enclosure-readback} to tie
the terminal finite window to the validated enclosure readback rows.

Next identify the common three-packet normal form. Apply
\autoref{thm:dyadicapproximation-dyadicmesh-validatednumerics-consumer-normal-form}
to the accepted dyadic packet, the mesh cell containing its transported
endpoint, and the validated enclosure over the same cell and containment
ledger. This produces one finite surface over the listed precision, endpoint,
mesh, regular-rational, real-readback, transport, continuation, provenance, and
local naming rows.

Now compare the routes. Apply
\autoref{thm:dyadicapproximation-validated-enclosure-route-commutation} to
identify the route that reads the terminal DyadicApproximation finite window
and then the $\RealUp$ seal with the route that passes through the DyadicMesh
cell and the ValidatedNumerics enclosure.

Finally attach the neighboring consumer boundaries. Apply
\autoref{thm:dyadicmesh-cell-containment-obligation} for the mesh level,
cell-index, rational-interval, containment-ledger, transport, continuation,
provenance, and local name rows. Apply
\autoref{thm:dyadicmesh-validatednumerics-handoff} and
\autoref{thm:validatednumerics-real-readback-soundness} to read the validated
enclosure as the same finite real-readback surface.

The carrier-exhaustion, normal-form, route-commutation, mesh-containment, and
validated-readback boundaries leave no coordinate for solver correctness,
floating-point semantics, host real equality, quotient reals, or classical
completeness. The three routes therefore expose exactly the single finite
$\RegSeqRatUp/\RealUp$ consumer surface stated above.
\end{proof}
