\begin{theorem}[DyadicApproximation terminal tail-budget Real-completion route]
\label{thm:dyadic-approximation-terminal-tail-budget-real-completion-route}
Let $T$ be an accepted terminal $\DyadicApproximationUp$ finite packet. Suppose $T$ is matched with a $\RealDiagonalCompletionUp$ packet $D$, a $\FiniteErrorBudgetUp$ request $B$, a $\DyadicTailBoundUp$ ledger row, a $\StreamNameUp$ window, a $\RegSeqRatUp$ readback, and a $\RealUp$ seal row by the displayed $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ rows of the terminal packet.

Then the matched packet exposes exactly the terminal budget-to-seal route: the finite budget request is read through the terminal precision row, the transported dyadic endpoint, the $\RationalIntervalUp$ cell, the $\DyadicMeshUp$ selector, the $\ValidatedNumericsUp$ enclosure, the stream window, the regular-rational readback, the dyadic tail-bound ledger, and the $\RealUp$ seal before it is presented to the Real-completion consumer surface. No completed real equality, quotient stream, host limit, solver oracle, or metric-completion object is exported by this route.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_terminal\_tail\_budget\_real\_completion\_route}
\begin{proof}
First normalize the terminal finite packet. The finite-packet Real readback theorem \autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback} places the terminal precision, endpoint, stream window, regular-rational readback, validated enclosure, $\RealUp$ seal, transports, continuation routes, package provenance, and local certificate on one finite surface.

Next attach the diagonal-completion side. The terminal diagonal readback composition theorem \autoref{thm:dyadicapproximation-terminal-diagonal-readback-composition} identifies the matched $\RealDiagonalCompletionUp$ packet with the same terminal precision, endpoint, stream window, readback, seal, transport, continuation, package, and certificate rows.

Now consume the mesh and budget rows. The terminal dyadic-net consumption theorem \autoref{thm:dyadicapproximation-terminal-dyadic-net-consumption} adds the $\RationalIntervalUp$ cell and $\DyadicMeshUp$ selector, while \autoref{thm:dyadicapproximation-terminal-tail-budget-exhaustion} forces the $\FiniteErrorBudgetUp$ request through the displayed $\DyadicTailBoundUp$ ledger and the same terminal seal route.

These cited surfaces share the same terminal rows. Repacking them gives precisely the budget-to-seal route stated above, and their non-escape clauses leave no coordinate for completed real equality, quotient streams, host limits, solver oracles, or metric-completion objects.
\end{proof}
