\begin{theorem}[DyadicApproximation terminal mesh enclosure compatibility]
\label{thm:dyadicapproximation-terminal-mesh-enclosure-compatibility}
Let an accepted finite $\DyadicApproximationUp$ packet have consumer read with
terminal displayed window $T$. For any downstream read through the
$\DyadicMeshUp$ standard finite mesh bridge and the $\ValidatedNumericsUp$
enclosure packet, the mesh cell and the validated enclosure consume the same
terminal window $T$.

Equivalently, the rational interval cell, dyadic endpoint-radius-order ledger,
$\RealUp$ boundary token, validated enclosure row, visible $\hsame$ rows,
visible $\Cont$ routes, $\mathsf{Pkg}$ provenance, and local $\NameCert$ rows
agree as one terminal finite surface. This common surface exports no completed
real, infinite mesh, solver correctness row, floating-point semantics row, or
compactness row.
\end{theorem}
\begin{proof}
First exhaust the accepted finite packet. Apply
\autoref{thm:dyadicapproximation-finite-packet-readback-exhaustion} to read the
terminal displayed packet as its precision row, dyadic endpoint and radius
rows, order ledger, regular-rational observation window, $\RealUp$ boundary
token, visible transports, continuation routes, package provenance, and local
certificate rows.

Next identify the terminal enclosure route. Apply
\autoref{thm:dyadicapproximation-terminal-validated-enclosure-readback}. The
validated enclosure row can see the finite dyadic approximation only through
the terminal displayed window $T$ and the rows listed there.

The mesh and enclosure consumers are then put into the same normal form. Apply
\autoref{thm:dyadicapproximation-dyadicmesh-validatednumerics-consumer-normal-form}
to identify the $\DyadicMeshUp$ cell row and the $\ValidatedNumericsUp$
containment row with the terminal precision, endpoint-radius-order, real
boundary, transport, continuation, provenance, and local certificate rows.

Finally use the standard finite mesh bridge,
\autoref{thm:dyadicmesh-standard-finite-mesh-bridge-boundary}. It states that
the displayed mesh read is exactly the rational interval cell read by the
downstream consumer. Combining the four cited readbacks leaves a single
terminal finite surface and no coordinate in which a completed real, infinite
mesh, solver correctness assertion, floating-point semantics assertion, or
compactness claim could be exported.
\end{proof}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_terminal\_mesh\_enclosure\_compatibility}
