\begin{theorem}[DyadicApproximation terminal validated enclosure readback]
\label{thm:dyadicapproximation-terminal-validated-enclosure-readback}
Let a compatible finite $\DyadicApproximationUp$ refinement chain have terminal
displayed window $T$. Suppose the prefix projection of the chain has stabilized
and the overlap refinement chain reads in the displayed overlap normal form. If
a $\DyadicMeshUp$ finite cell and a $\ValidatedNumericsUp$ enclosure consume
that same terminal window, then the terminal readback surface is exactly the
same finite enclosure surface consumed by those two downstream packets.

Componentwise, the common surface consists of the terminal precision row, the
dyadic endpoint and radius route, the $\RegSeqRatUp$ observation window, the
$\DyadicMeshUp$ rational-interval cell row, the $\ValidatedNumericsUp$
containment ledger, the $\RealUp$ readback token, the visible $\hsame$
transports, the visible $\Cont$ routes, the $\Pkg$ provenance rows, and the
local $\NameCert$ rows. The readback does not assert solver correctness,
floating-point semantics, classical real completeness, or host real equality.
\end{theorem}
\begin{proof}
First stabilize the terminal dyadic window. Apply
\autoref{thm:dyadicapproximation-terminal-window-prefix-projection} to identify
every prefix read with the corresponding row of $T$: precision, endpoint,
regular-rational observation, real-seal token, visible transport, continuation,
provenance, and local certificate rows.

Next stabilize overlap access. Apply
\autoref{thm:dyadicapproximation-overlap-refinement-chain-normal-form}. The
overlap read has the same terminal precision row, transported endpoint route,
rational-interval window, $\RegSeqRatUp$ readback, $\RealUp$ seal boundary,
visible $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance, and
local $\NameCert_{\DyadicApproximationUp}$ rows.

Now pass to the finite cell and enclosure consumers. By
\autoref{thm:dyadicapproximation-dyadicmesh-validatednumerics-consumer-normal-form},
the $\DyadicMeshUp$ cell and the $\ValidatedNumericsUp$ enclosure read the
dyadic terminal window only through the displayed precision row, endpoint row,
rational-interval cell row, mesh level and cell-index rows, validated
containment ledger, regular-rational readback, real-seal token, transport
routes, provenance, and local certificate rows.

The mesh handoff and the enclosure boundary identify the downstream rows.
Apply \autoref{thm:dyadicmesh-validatednumerics-handoff} for the rational
interval cell, containment ledger, endpoint readback, and mesh provenance.
Apply \autoref{thm:validatednumerics-validated-enclosure-bridge-boundary} for
the validated enclosure row, precision request, containment ledger, real-name
readback token, transport rows, continuation routes, package provenance, and
local certificate row.

Repack the identified rows as one finite readback surface. The preceding
steps account for every component listed in the theorem statement, and the
cited consumer boundaries contain no coordinate for solver correctness,
floating-point semantics, classical real completeness, or host real equality.
\end{proof}
