\begin{theorem}[DyadicApproximation terminal diagonal completion handoff]
\label{thm:dyadicapproximation-terminal-diagonal-completion-handoff}
Let $T$ be an accepted terminal $\DyadicApproximationUp$ finite packet and
let $D$ be an accepted $\RealDiagonalCompletionUp$ packet. Suppose the
terminal route of $T$ and the diagonal row of $D$ display the same terminal
precision, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback,
transported dyadic endpoint, $\RealUp$ seal ledger, visible $\hsame$
transports, visible $\Cont$ routes, $\Pkg$ provenance, and local
$\NameCert_{\DyadicApproximationUp}$ and
$\NameCert_{\RealDiagonalCompletionUp}$ provenance.

Then the $\RealUp$ consumer route through $T$ and the $\RealUp$ consumer
route through $D$ expose the same finite surface: terminal precision,
transported dyadic endpoint, scheduled stream window, regular-rational
readback, $\RealUp$ seal ledger, visible $\hsame$ transports, visible
$\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ provenance.

The handoff is only this finite BEDC surface. It does not assert completed
real equality, quotient streams, selected host limits, solver correctness, or
choice-selected completion points.
\end{theorem}
\begin{proof}
First normalize the terminal packet route. Apply
\autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback} to
$T$. The terminal consumer is thereby read through the displayed terminal
precision, transported endpoint, scheduled $\StreamNameUp$ window,
$\RegSeqRatUp$ readback, $\RealUp$ seal row, transport rows, continuation
routes, package provenance, and local dyadic certificate.

Next normalize the diagonal-completion route. Apply
\autoref{thm:real-diagonal-completion-window-extraction} to $D$ to expose the
diagonal selector, scheduled window, and regular-rational readback selected by
the requested row. Apply
\autoref{thm:real-diagonal-completion-seal-factorization} to factor the
$\RealUp$ seal ledger through those same extracted finite windows and
readback rows.

The hypotheses identify the scheduled window and readback rows on the two
routes, together with the terminal precision, transported endpoint, seal
ledger, transports, continuations, package provenance, and local
certificates. Repacking those identified coordinates gives one shared finite
surface for both $\RealUp$ consumers.

The cited dyadic and diagonal boundaries expose only finite packet data.
Consequently the repacked surface has no coordinate for completed real
equality, quotient streams, selected host limits, solver correctness, or
choice-selected completion points.
\end{proof}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_terminal\_diagonal\_completion\_handoff}
