\begin{theorem}[DyadicApproximation nested window exhaustion]
\label{thm:dyadicapproximation-nested-window-exhaustion}
Every finite chain of compatible $\DyadicApproximationUp$ consumer refinements
has one terminal displayed window. Every consumer read in the chain factors
through exactly the terminal precision row, the $\DyadicRatCoreUp$ endpoint
row, the $\StreamNameUp$ and $\RegSeqRatUp$ observation window, the displayed
$\hsame$ transports, the visible $\Cont$ routes, $\mathsf{Pkg}$ provenance,
and the local $\NameCert_{\DyadicApproximationUp}$ ledger.

When a $\RationalIntervalUp$ containment row is present in the chain, it is
read through that same terminal window. The exhaustion exports no quotient
real, host equality, completion point, trichotomy row, selected representative,
located subset, or choice principle.
\end{theorem}
\begin{proof}
Induct over the finite refinement chain. The empty and singleton chains are
handled by projecting the accepted packet carrier: the only consumer-visible
rows are the displayed precision row, endpoint row, observation window,
transport routes, package provenance, and local naming ledger.

For the binary extension step, apply
\autoref{thm:dyadicapproximation-terminal-refinement-window} to the terminal
window already obtained for the initial segment and to the next compatible
refinement packet. This produces one displayed terminal precision row for the
extended chain.

Use
\autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}
to remove dependence on the chosen bracketing of the finite chain. Any two
ways of building the terminal window identify the same consumer-visible
precision, endpoint, observation, transport, package, and ledger rows.

Finally apply \autoref{thm:dyadicapproximation-consumer-completeness}. It
exhausts all finite consumer reads through the terminal row, while
\autoref{thm:dyadic-approximation-rational-interval-window-handoff} accounts
for the containment row when present. Since the carrier contains none of the
excluded completion, quotient, trichotomy, selection, located-subset, or choice
coordinates, the nested chain exports none of them.
\end{proof}

\begin{theorem}[DyadicApproximation terminal window idempotence]
\label{thm:dyadicapproximation-terminal-window-idempotence}
Let a compatible finite $\DyadicApproximationUp$ refinement chain have terminal
displayed window $T$. If $T$ is adjoined as one further compatible refinement,
then the extended chain has the same terminal precision row, dyadic endpoint
row, $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealUp$ seal ledger,
optional $\RationalIntervalUp$ containment row, visible $\hsame$ transports,
visible $\Cont$ transports, $\mathsf{Pkg}$ provenance, and local
$\NameCert_{\DyadicApproximationUp}$ ledger as the original chain.

Thus repeating a terminal displayed window contributes no consumer-visible row.
The extended read exports no quotient-real equality, host equality, completed
real, choice principle, or selected representative coordinate beyond the rows
already present in $T$.
\end{theorem}
\begin{proof}
Start with the original finite chain. Apply
\autoref{thm:dyadicapproximation-terminal-refinement-window} to obtain its
terminal displayed window $T$ and the listed precision, endpoint, observation,
seal, transport, package, containment, and local certificate rows.

Now append $T$ as a compatible refinement packet. Applying
\autoref{thm:dyadicapproximation-terminal-refinement-window} again produces a
terminal row for the extended chain, but the new binary refinement step uses the
same displayed terminal precision row as both the accumulated window and the
adjoined packet.

Use
\autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}
to compare the bracketing that first forms $T$ with the bracketing that first
forms $T$ and then appends $T$. Associativity identifies the consumer-visible
precision, endpoint, stream, regular-sequence, seal, containment, transport,
package, and local ledger rows in the two bracketings.

Finally apply \autoref{thm:dyadicapproximation-consumer-completeness}. Since
all finite consumer reads factor through those identified rows, the appended
terminal window has no additional quotient-real, host-equality, completion,
choice, or selected-representative coordinate to export.
\end{proof}

\begin{theorem}[DyadicApproximation terminal window subchain absorption]
\label{thm:dyadicapproximation-terminal-window-subchain-absorption}
Let a compatible finite $\DyadicApproximationUp$ refinement chain have terminal
displayed window $T$. Any finite compatible subchain whose packets factor
through $T$ may be inserted, deleted, or repeated without changing the terminal
precision row, dyadic endpoint row, $\StreamNameUp$ window,
$\RegSeqRatUp$ readback, $\RealUp$ seal ledger, optional
$\RationalIntervalUp$ containment row, visible $\hsame$ routes, visible
$\Cont$ routes, $\mathsf{Pkg}$ provenance, or local
$\NameCert_{\DyadicApproximationUp}$ ledger.

Equivalently, the displayed terminal row is an absorbing finite normal form for
every already-terminal compatible subchain. The normal form exports no quotient
real equality, host equality, completed real, trichotomy, choice principle, or
selected representative coordinate beyond the rows already visible through
$T$.
\end{theorem}
\begin{proof}
Begin with the given finite chain and apply
\autoref{thm:dyadicapproximation-nested-window-exhaustion}. This places every
compatible finite refinement packet in the same directed displayed-window
spine and supplies the common precision, endpoint, stream, regular-sequence,
seal, containment, transport, package, and local certificate rows.

For a subchain whose packets factor through $T$, apply
\autoref{thm:dyadicapproximation-terminal-window-idempotence} to each displayed
terminal packet in the subchain. Repetition of such a packet contributes no new
consumer-visible row, and deletion removes only rows already identified with
the terminal row.

It remains to compare the positions of the subchain inside the whole finite
refinement. Use
\autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}
to rebracket the refinement so the subchain is read either before, after, or at
the displayed terminal row. The associated bracketings have the same precision,
endpoint, stream, regular-sequence, seal, containment, visible transport,
package, and local ledger data.

Finally apply \autoref{thm:dyadicapproximation-consumer-completeness}. Every
finite $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and optional
$\RationalIntervalUp$ consumer read factors through the terminal displayed row,
so insertion, deletion, and repetition of an already-terminal compatible
subchain leave exactly the same public finite-window surface.
\end{proof}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_terminal\_refinement\_subchain\_absorption}

\begin{theorem}[DyadicApproximation window RegSeqRat source exhaustion]
\label{thm:dyadicapproximation-window-regseqrat-source-exhaustion}
Every accepted $\DyadicApproximationUp$ packet together with a finite
compatible refinement chain determines exactly one displayed
$\RegSeqRatUp$-facing source surface. The surface consists of the unary
precision row, the $\DyadicRatCoreUp$ endpoint row, the $\StreamNameUp$
schedule, the $\RegSeqRatUp$ observation window, the $\RealUp$ seal ledger,
the visible $\hsame$ transports, the visible $\Cont$ routes, the
$\mathsf{Pkg}$ provenance row, and the local
$\NameCert_{\DyadicApproximationUp}$ row.

If the same packet is read through the $\RationalIntervalUp$ handoff or the
$\RealUp$ seal boundary, those consumers read that same source surface and no
other row. The exhaustion exports no quotient real equality, selected limit,
trichotomy row, located subset, or choice principle.
\end{theorem}
\begin{proof}
Start with the finite refinement chain and apply
\autoref{thm:dyadicapproximation-nested-window-exhaustion}. This gives one
terminal displayed window containing the precision, endpoint, stream,
regular-sequence, transport, continuation, package, and local certificate rows
seen by every consumer read in the chain.

Next apply \autoref{thm:dyadicapproximation-real-seal-scope}. The
$\RealUp$ seal ledger is a finite boundary row attached to the same terminal
window, so it does not contribute a completed real or a selected limit outside
the displayed packet surface.

Use \autoref{thm:dyadic-approximation-real-seal-handoff} to read the terminal
window as a real-seal source for $\RegSeqRatUp$. The handoff identifies the
regular rational observation row, seal ledger, visible $\hsame$ route, visible
$\Cont$ route, and package provenance as the only real-facing source data.

Finally apply
\autoref{thm:dyadic-approximation-rational-interval-window-handoff}. It shows
that any rational-interval consumer sees the same endpoint and observation
rows, so the terminal window is the unique displayed source surface for all
the named consumers. Since all cited surfaces are finite packet rows, quotient
real equality, selected limits, trichotomy, located subsets, and choice
principles are not exported.
\end{proof}

\begin{theorem}[DyadicApproximation overlap-directed seal exhaustion]\label{thm:dyadicapproximation-overlap-directed-seal-exhaustion}
Let two accepted $\DyadicApproximationUp$ packets carry overlapping finite
$\StreamNameUp$ windows and overlapping finite $\RegSeqRatUp$ observation
windows. Suppose their overlap is equipped with a displayed directed common
unary precision refinement, so that both dyadic endpoints and both seal
ledgers are transported to the same visible precision row. Then every
$\RealUp$ seal read from either packet factors through one finite boundary
surface: the common precision row, the transported dyadic endpoints, the
$\RationalIntervalUp$ refinement window, the $\RegSeqRatUp$ source readback,
the visible $\hsame$ transports, the visible $\Cont$ routes, $\mathsf{Pkg}$
provenance, and the local $\NameCert_{\DyadicApproximationUp}$ rows.

This finite boundary exports no quotient-real equality, host real equality,
completion point, trichotomy row, selected representative, located subset, or
choice principle. The overlap theorem is only a coverage statement for the
displayed finite rows already present in the two accepted packets and their
directed refinement data.
\end{theorem}
\begin{proof}
First put the two accepted packets on the same displayed precision row. Apply
\autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}
to make the directed refinement independent of the binary route used to reach
the common row.

Next apply \autoref{thm:dyadicapproximation-terminal-refinement-window} to the
overlapping two-packet family. This produces the terminal finite window
containing the common precision row, transported endpoints, stream window,
regular rational observation window, seal ledger, visible transports,
continuations, package provenance, and local certificate rows.

Use \autoref{thm:dyadic-approximation-rational-interval-window-handoff} to
read the transported dyadic endpoints through the shared
$\RationalIntervalUp$ refinement window. The handoff keeps the endpoint and
containment data inside the same finite overlap surface.

Then apply
\autoref{thm:dyadicapproximation-window-regseqrat-source-exhaustion}. It
identifies the $\RegSeqRatUp$ source readback and shows that both
$\RationalIntervalUp$ and $\RealUp$ consumers read the same displayed source
surface.

Finally route the seal boundary through
\autoref{thm:dyadicapproximation-real-seal-scope}. Since the seal scope has no
coordinate for quotient-real equality, host equality, completion points,
trichotomy, selected representatives, located subsets, or choice data, the
overlap-directed read cannot export any of those objects.
\end{proof}

\begin{theorem}[DyadicApproximation overlap seal idempotence]\label{thm:dyadicapproximation-overlap-seal-idempotence}
Let two accepted $\DyadicApproximationUp$ packets satisfy the hypotheses of
\autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion}, and let
their resulting finite $\RealUp$ seal boundary be read again through any
compatible displayed overlap refinement. Then the second read factors through
the same common precision row, the same transported dyadic endpoint rows, the
same $\RationalIntervalUp$ refinement window, the same $\RegSeqRatUp$ source
readback, the same visible $\hsame$ transports, the same visible $\Cont$
routes, the same $\mathsf{Pkg}$ provenance, and the same local
$\NameCert_{\DyadicApproximationUp}$ rows as the first seal read.

Thus repeated $\RealUp$ seal reads through a fixed finite overlap boundary are
idempotent as displayed packet reads. The idempotence assertion exports no
quotient-real equality, host real equality, completion point, trichotomy row,
selected representative, located subset, or choice principle.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion} to the two
accepted packets and their displayed directed common precision refinement. This
identifies the first $\RealUp$ seal read with the finite overlap boundary
containing the common precision row, transported endpoint rows, rational
interval window, regular rational source readback, visible transports,
continuations, package provenance, and local certificate rows.

Next apply \autoref{thm:dyadicapproximation-terminal-window-idempotence} to the
compatible displayed overlap refinement used by the second read. Re-reading a
terminal finite window through a compatible refinement returns the same terminal
window, so the second seal read cannot introduce a new precision row, endpoint
row, consumer route, package row, or local certificate row.

Finally apply
\autoref{thm:dyadicapproximation-window-regseqrat-source-exhaustion}. It
identifies the unique $\RegSeqRatUp$-facing source surface seen by the
$\RationalIntervalUp$ and $\RealUp$ consumers, and therefore transports the
second seal read back to the same source surface already named by the first
overlap-directed read. Since each cited result is a statement about finite
displayed packet rows, the repeated read has no coordinate for quotient-real
equality, host real equality, completion points, trichotomy, selected
representatives, located subsets, or choice data.
\end{proof}

\begin{theorem}[DyadicApproximation overlap refinement chain normal form]\label{thm:dyadicapproximation-overlap-refinement-chain-normal-form}
Let two accepted $\DyadicApproximationUp$ packets satisfy the overlap
hypotheses of \autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion}.
For every finite chain of compatible displayed overlap refinements, every
repeated $\RealUp$ seal read factors through one terminal normal-form packet.
This packet consists exactly of the common precision row, the transported
dyadic endpoint rows, the $\RationalIntervalUp$ refinement window, the
$\RegSeqRatUp$ source readback, visible $\hsame$ transports, visible $\Cont$
routes, $\mathsf{Pkg}$ provenance, and the local
$\NameCert_{\DyadicApproximationUp}$ rows.

The normal form is a finite displayed packet normal form for overlap reads. It
does not contain quotient-real equality, host equality, completion points,
trichotomy rows, selected representatives, located subsets, or choice data.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion}. The first
common overlap boundary supplies the displayed precision row, transported
endpoints, rational-interval window, regular rational readback, visible
transport routes, package provenance, and local certificate rows shared by the
two accepted packets.

Next run the finite compatible refinement chain through
\autoref{thm:dyadicapproximation-terminal-window-idempotence}. Once the common
boundary has been read as a terminal displayed window, compatible re-reading
stabilizes at the same terminal packet and cannot add a second endpoint,
precision, route, provenance, or certificate row.

Then apply
\autoref{thm:dyadicapproximation-window-regseqrat-source-exhaustion}. This
identifies the unique $\RegSeqRatUp$-facing source surface seen by both the
$\RationalIntervalUp$ window and the repeated $\RealUp$ seal reads, so the
terminal packet is the single source normal form for the whole chain.

Finally apply \autoref{thm:dyadicapproximation-real-seal-scope}. The
$\RealUp$ boundary has only the displayed seal rows named above, so the
normal-form packet excludes quotient-real equality, host equality, completion
points, trichotomy rows, selected representatives, located subsets, and choice
data.
\end{proof}

\begin{theorem}[DyadicApproximation overlap coarsening seal stability]\label{thm:dyadicapproximation-overlap-coarsening-seal-stability}
Let two accepted $\DyadicApproximationUp$ packets satisfy
\autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion}. Suppose
both packets are weakened to a common coarser unary precision row through the
displayed $\DyadicRatCoreUp$ radius ledger. Then every compatible $\RealUp$
seal reread factors through the same finite overlap surface, now read at the
coarser precision row with transported endpoints, the
$\RationalIntervalUp$ refinement window, the $\RegSeqRatUp$ readback, visible
$\hsame$ and $\Cont$ routes, $\mathsf{Pkg}$ provenance, and the local
$\NameCert_{\DyadicApproximationUp}$ rows.

The coarsened reread exports no quotient-real equality, host real equality,
completion point, trichotomy row, selected representative, located subset, or
choice principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:dyadic-approximation-precision-weakening} to each accepted
packet, using the displayed $\DyadicRatCoreUp$ radius ledger to transport the
endpoint and seal rows to the common coarser precision row.

Next use
\autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}
to identify the two weakening routes with one directed coarsening surface. The
common row therefore carries the same transported endpoint, interval, stream,
regular-sequence, transport, continuation, package, and local certificate
data.

Apply \autoref{thm:dyadicapproximation-overlap-directed-seal-exhaustion} on
this coarser row. It supplies the finite overlap boundary seen by the
$\RealUp$, $\RationalIntervalUp$, and $\RegSeqRatUp$ consumers.

Finally apply \autoref{thm:dyadicapproximation-overlap-seal-idempotence}. A
compatible reread of the already displayed seal boundary remains on that same
finite boundary, so no completed real, host equality, representative choice,
located subset, trichotomy, or choice data can be exported.
\end{proof}

\closureat{DyadicApproximationUp}{seedStr}
\closureat{DyadicApproximationUp}{obligationStr}
\closureat{DyadicApproximationUp}{scopedStr}
\closureat{DyadicApproximationUp}{publicStr}
\closureat{DyadicApproximationUp}{bridgedStr}
\closureat{DyadicApproximationUp}{matureStr}

\begin{closurestatus}{\DyadicApproximationUp}
  \constructivestory{A finite dyadic approximation packet is generated from a unary precision row, a displayed $\DyadicRatCoreUp$ endpoint, a $\StreamNameUp$ and $\RegSeqRatUp$ finite observation window, a $\RealUp$ seal ledger, visible $\hsame$ and $\Cont$ transport, and $\mathsf{Pkg}$ provenance.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:dyadicapproximation-window-scope}, \autoref{thm:dyadicapproximation-real-seal-scope}, \autoref{thm:dyadicapproximation-ledger-exclusion-scope}, \autoref{thm:dyadicapproximation-public-finite-window-export}, \autoref{thm:dyadic-approximation-standard-finite-approximation-bridge}, \autoref{thm:dyadic-approximation-rational-interval-window-handoff}, \autoref{thm:dyadicapproximation-consumer-completeness}, \autoref{thm:dyadicapproximation-directed-precision-refinement-associativity}, and \autoref{thm:dyadicapproximation-terminal-refinement-window} form the public finite-window export, standard finite dyadic-approximation readback, rational interval handoff, finite consumer surface, directed refinement associativity, and terminal common-refinement window for the accepted dyadic window, $\RealUp$ seal handoff, and ledger exclusions over $\mathsf{BHist}$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RationalIntervalUp$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close quotient reals, host real equality, completion points, or choice-selected representatives.}
  \upgradepath{No further paper theory-axis grade remains; formal verification remains a separate axis for the same dyadic approximation packet.}
\end{closurestatus}
