\begin{theorem}[DyadicApproximation terminal diagonal readback composition]
\label{thm:dyadicapproximation-terminal-diagonal-readback-composition}
Let $T$ be an accepted terminal $\DyadicApproximationUp$ finite packet and let $D$ be an accepted $\RealDiagonalCompletionUp$ packet. Suppose $T$ has the finite-packet $\RealUp$ readback surface of \autoref{thm:dyadicapproximation-terminal-finite-packet-real-readback}, and suppose $T$ and $D$ are matched by the terminal diagonal handoff of \autoref{thm:dyadicapproximation-terminal-diagonal-completion-handoff}.

Then every $\RealUp$ consumer route through the matched diagonal-completion packet factors through the same terminal precision, transported dyadic endpoint, $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealUp$ seal, visible $\hsame$ rows, visible $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\DyadicApproximationUp}$ and $\NameCert_{\RealDiagonalCompletionUp}$ rows already exposed by the terminal packet. The composition exports no completed real equality, quotient stream, selected host limit, solver correctness, or choice-selected completion point.
\end{theorem}
\begin{proof}
First normalize the terminal dyadic packet. The finite-packet readback theorem factors every terminal $\RealUp$ read through the displayed terminal precision, endpoint, stream-name window, regular-rational readback, real seal, transport rows, continuation routes, package provenance, and local dyadic certificate.

Next apply the terminal diagonal handoff. Its hypotheses identify the terminal route of $T$ with the diagonal row of $D$ across the same precision, endpoint, scheduled window, readback, seal ledger, transports, continuations, package provenance, and local certificate rows.

Composing these two surfaces gives one finite route for the diagonal-completion consumer. The readback data first appears in the terminal dyadic packet and is then repacked as the diagonal-completion handoff, so the $\RealUp$ consumer sees the same finite rows in the same terminal precision boundary.

The two cited theorems carry the same non-escape boundary. Therefore the composite surface has no coordinate for completed real equality, quotient streams, selected host limits, solver correctness, or choice-selected completion points.
\end{proof}
