\begin{theorem}[DyadicApproximation validated enclosure route commutation]
\label{thm:dyadicapproximation-validated-enclosure-route-commutation}
Let $A=(n,d,w,l,p)$ be an accepted $\DyadicApproximationUp$ packet. Let
$M=(\ell,J,I,E,H,C,P,N)$ be an accepted $\DyadicMeshUp$ cell whose
$\RationalIntervalUp$ row $I$ contains the transported dyadic endpoint $d$ at
the displayed precision $n$. Let $V$ be an accepted $\ValidatedNumericsUp$
enclosure over that same cell and containment ledger.

The route that first reads $A$ through
\autoref{thm:dyadicapproximation-public-finite-window-export} and then exposes
the $\RealUp$ seal boundary reads exactly the same finite
$\RegSeqRatUp/\RealUp$ consumer surface as the route that first reads $M$
through \autoref{thm:dyadicmesh-validatednumerics-handoff} and then exposes
$V$ through
\autoref{thm:validatednumerics-validated-enclosure-bridge-boundary}. The common
surface consists precisely of the precision row, transported dyadic endpoint,
rational-interval cell, mesh level and cell index, regular rational
observation window, validated containment ledger, real readback token, visible
$\hsame$ transports, visible $\Cont$ routes, $\mathsf{Pkg}$ provenance, and
local $\NameCert$ rows.

This correspondence does not assert solver correctness, floating-point
semantics, quotient-real equality, host real equality, or classical
completeness.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicApproximationUp.DyadicApproximationCarrier\_validated\_enclosure\_route\_commutation}
\begin{proof}
First normalize the three packets together. Apply
\autoref{thm:dyadicapproximation-dyadicmesh-validatednumerics-consumer-normal-form}
to the accepted dyadic approximation packet, the mesh cell containing its
transported endpoint, and the validated enclosure over the same cell. This
produces one finite consumer surface over the listed precision, endpoint,
mesh, regular-rational, real-seal, transport, continuation, provenance, and
local certificate rows.

Next identify the dyadic route. Apply
\autoref{thm:dyadicapproximation-terminal-window-prefix-projection} to replace
every finite prefix read of $A$ by the terminal displayed window, and apply
\autoref{thm:dyadicapproximation-public-finite-window-export} to read the
public packet through that finite window. The $\RealUp$ seal therefore remains
attached to the same $\RegSeqRatUp$ observation window and dyadic endpoint row.

Now identify the mesh and enclosure route. Apply
\autoref{thm:dyadicmesh-rationalinterval-coverage} to read the mesh cell as
the rational interval containing the transported endpoint, and apply
\autoref{thm:dyadicmesh-validatednumerics-handoff} to pass that cell to the
validated enclosure surface.

Finally apply
\autoref{thm:validatednumerics-validated-enclosure-bridge-boundary} and
\autoref{thm:validatednumerics-finite-consumer-example-completeness}. These
theorems say that the validated route exposes exactly the same finite
rational-interval, regular-rational, real-readback, containment, transport,
continuation, provenance, and local certificate rows. Repacking those rows
gives the claimed route commutation, while the excluded semantic obligations
remain outside every cited boundary.
\end{proof}
