\chapter{A Concrete Naming Certificate for $\RationalCauchyTelescopeUp$}
\label{ch:concrete-instances-rational-cauchy-telescope-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy real names, the $\RationalCauchyTelescopeUp$ packet records the finite telescoping route by which rational step rows become a regular Cauchy readback before any completed-real assertion is available. It sits after rational rows from \autoref{ch:concrete-instances-rat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite L10 route for Real and Completion consumers; it does not assert quotient streams, selected limits, trichotomy, choice, or ambient $\RealUp$ completeness.

\begin{definition}[RationalCauchyTelescope carrier]
\label{def:rational-cauchy-telescope-carrier}
A $\RationalCauchyTelescopeUp$ carrier is a finite $\BHist$ packet
$$
T=(Q,D,W,R,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the finite $\RatUp$ rational-step ledger, indexed by the same observation stages that the downstream stream window reads.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row that bounds the visible tail of the rational step rows.
\item $W$ is the $\StreamNameUp$ finite-window row exposing exactly the observation stages used by $Q$ and $D$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained by summing the displayed rational step rows over the windows in $W$.
\item $M$ is the telescoping modulus row saying that every accepted tail comparison is discharged by the dyadic budget in $D$.
\item $H$ records componentwise $\hsame$ transport for $Q,D,W,R,M,C,P,N$.
\item $C$ records displayed $\Cont$ replay of the finite telescoping computation and its tail comparisons.
\item $P$ is the $\Pkg$ provenance over $\RationalCauchyTelescopeUp$, $\RatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RationalCauchyTelescopeUp}$ row.
\end{enumerate}
The carrier contains no quotient stream equality, selected limit, trichotomy decision, choice principle, or ambient $\RealUp$ completeness coordinate.
\end{definition}

\begin{theorem}[RationalCauchyTelescope NameCert obligations]
\label{thm:rational-cauchy-telescope-namecert-obligations}
For every accepted $\RationalCauchyTelescopeUp$ carrier
$$
T=(Q,D,W,R,M,H,C,P,N),
$$
the local $\NameCert_{\RationalCauchyTelescopeUp}$ surface consists exactly of rational-step admission, dyadic tolerance visibility, finite-window exposure, regular rational readback, telescoping-modulus discharge, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every obligation is read through the finite route
$$
\RatUp,\quad \DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp .
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:rational-cauchy-telescope-carrier}. The only mathematical rows available to a consumer are $Q,D,W,R,M$ together with the structural rows $H,C,P,N$.

The rational-step ledger $Q$ supplies the finite addends, while $W$ supplies the observation stages on which those addends may be read. The dyadic row $D$ fixes the tolerance budget for tail comparisons on the same windows.

The readback row $R$ is obtained by displayed finite summation over $Q$ and $W$. The modulus row $M$ then records that every accepted telescoping tail comparison is bounded by the dyadic budget from $D$.

Transport, replay, provenance, and local naming are confined to $H,C,P,N$. Since no quotient-stream, selected-limit, trichotomy, choice, or completeness coordinate occurs in the packet, the listed rows exhaust the NameCert obligation surface.
\end{proof}

\begin{theorem}[RationalCauchyTelescope RegSeqRat factorization]
\label{thm:rational-cauchy-telescope-regseqrat-factorization}
Every Real-facing or Completion-facing read of an accepted $\RationalCauchyTelescopeUp$ packet factors through the displayed chain
$$
Q \longmapsto W \longmapsto D \longmapsto M \longmapsto R,
$$
before it can expose a $\RealUp$ seal. Thus the $\RegSeqRatUp$ readback is sourced by finite rational step rows, finite StreamName windows, and a dyadic telescoping modulus, not by quotient streams, selected representatives, trichotomy, choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from an accepted carrier $T=(Q,D,W,R,M,H,C,P,N)$. The rational step rows $Q$ can be inspected only through the finite windows $W$, and the same windows carry the dyadic tolerance row $D$.

The telescoping modulus $M$ is read after $Q,W,D$. It is the row that converts finite step sums into tail comparisons suitable for the regular rational readback.

Finally the readback row $R$ is the only $\RegSeqRatUp$ coordinate in the packet. Any Real-facing seal therefore receives its regular rational name through $R$ after the finite telescoping route has been displayed.

Because the carrier has no further coordinate for quotient stream equality, selected representatives, trichotomy, choice, or ambient completeness, no completion consumer can bypass the displayed factorization.
\end{proof}

\closureat{RationalCauchyTelescopeUp}{seedStr}

\begin{closurestatus}{\RationalCauchyTelescopeUp}
  \constructivestory{A $\RationalCauchyTelescopeUp$ packet is generated from RatUp rational step rows, a DyadicRatCoreUp tolerance ledger, StreamName finite windows, a RegSeqRatUp readback, a telescoping modulus row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rational-cauchy-telescope-carrier}, \autoref{thm:rational-cauchy-telescope-namecert-obligations}, and \autoref{thm:rational-cauchy-telescope-regseqrat-factorization} seed the finite telescoping route from rational step rows to regular rational readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient streams, selected limits, trichotomy, choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked rational-step admission, dyadic tolerance stability, finite-window exposure, regular rational readback, telescoping-modulus discharge, and ledger non-escape for BEDC.Derived.RationalCauchyTelescopeUp.}
\end{closurestatus}
