\begin{theorem}[Bounded monotone Cauchy witness tail envelope public export]
\label{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let
$$
E=(S,F,\sigma,\mu,\lambda,I,H,C,P,N)
$$
be its scheduled tail envelope. The envelope $E$ exports the single public pre-seal service for completion-facing consumers: source reads pass through $S$, regular rational reads pass through $F$, window requests pass through $\sigma$, tolerance answers pass through $\mu$, dyadic and upper-bound budget reads pass through $\lambda$, trap reads pass through $I$, and the transport, continuation, provenance, and naming routes pass through $H,C,P,N$.

Thus every public tail-envelope read is already a read through $S,F,\sigma,\mu,\lambda,I,H,C,P,N$ before the $\RealUp$ seal row $Q$ is consumed. The export contains no selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_tail\_envelope\_public\_export}
\begin{proof}
Start with the scheduled windows. By \autoref{thm:bounded-monotone-cauchy-witness-window-coverage}, the source, regular-sequence, Cauchy witness, dyadic ledger, and trap-facing reads all pass through $S,F,\sigma,\mu,\lambda,I$ on the same displayed window schedule.

Next use the finite-read route. By \autoref{thm:bounded-monotone-cauchy-witness-finite-observation-lock}, Real-facing finite observations are locked to the displayed rows of $W$, so the public pre-seal route cannot replace $S,F,\sigma,\mu,\lambda,I$ by an unrecorded completion object.

The exactness and handoff theorems identify the public boundary. Apply \autoref{thm:bounded-monotone-cauchy-witness-trap-seal-exactness} to keep the located trap exact for the same envelope $E$, and apply \autoref{thm:bounded-monotone-cauchy-witness-seal-handoff} to locate the later $\RealUp$ seal after the displayed pre-seal service.

Finally, \autoref{thm:bounded-monotone-cauchy-witness-window-exhaustion} rules out any second tail service. Since the accepted packet exposes no coordinate beyond the listed rows, the envelope exports exactly the public service $S,F,\sigma,\mu,\lambda,I,H,C,P,N$ before $Q$ is read.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness completion consumer non-escape]
\label{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let $E=(S,F,\sigma,\mu,\lambda,I,H,C,P,N)$ be its scheduled tail envelope. Every completion-facing consumer of the bounded monotone Cauchy witness factors through the public envelope $E$, the $\RealObservationBudgetUp$ finite-read route, the $\RegSeqRatUp$ handoff, the $\LocatedIntervalUp$ trap, and the $\RealUp$ seal.

Consequently the consumer has no escape route to a selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector. Its entire public dependency surface is the finite package $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_completion\_consumer\_nonescape}
\begin{proof}
First build the envelope route. The public export theorem above identifies $E$ as the only pre-seal service, and \autoref{thm:bounded-monotone-cauchy-witness-window-coverage} keeps every inspected source and tail window on that service.

Next attach finite observation. By \autoref{thm:bounded-monotone-cauchy-witness-finite-observation-lock}, every Real-facing finite read is routed through the displayed finite rows of $W$. The regular rational handoff is the $F$ coordinate of that same packet, and the window ledger is the shared $\sigma,\mu,\lambda$ route.

The trap and seal then close the route. Apply \autoref{thm:bounded-monotone-cauchy-witness-trap-seal-exactness} to keep $I$ exact for the scheduled envelope, and apply \autoref{thm:bounded-monotone-cauchy-witness-seal-handoff} to pass from the trap side to the $\RealUp$ seal row $Q$ without introducing a second completion-facing input.

It remains to exclude escapes. \autoref{thm:bounded-monotone-cauchy-witness-root-unblock} gives the root consumer exactly the finite package $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, while \autoref{thm:bounded-monotone-cauchy-witness-window-exhaustion} rules out a hidden tail service. Therefore any completion-facing consumer factors through the displayed envelope, finite-read route, regular-sequence handoff, located trap, and seal, and no selected limit, equality principle, completeness principle, compactness row, or choice-like selector is exposed.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness completion consumer apartness budget]
\label{thm:bounded-monotone-cauchy-witness-completion-consumer-apartness-budget}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let $E=(S,F,\sigma,\mu,\lambda,I,H,C,P,N)$ be its scheduled tail envelope. Every completion-facing consumer of $W$ must consume the scheduled tail envelope $E$ together with the finite apartness and budget rows $\sigma,\mu,\lambda,I$ before it consumes the $\RealUp$ seal row $Q$.

Consequently the route cannot be read as a selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector. The only public pre-seal completion data are the scheduled envelope and the finite apartness-budget rows already displayed by $W$.
\end{theorem}
\begin{proof}
Start with the public export theorem. \autoref{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export} identifies $E$ as the exported pre-seal service and lists $\sigma,\mu,\lambda,I$ among the rows read before the seal.

Next use the finite-observation lock. By \autoref{thm:bounded-monotone-cauchy-witness-finite-observation-lock}, every Real-facing finite read remains on the displayed rows of $W$, so no consumer can replace the apartness and budget schedule by an unrecorded completion object.

The trap and seal then fix the order of consumption. Apply \autoref{thm:bounded-monotone-cauchy-witness-trap-seal-exactness} to keep $I$ on the same located trap surface, and apply \autoref{thm:bounded-monotone-cauchy-witness-seal-handoff} to place the $\RealUp$ seal row $Q$ after that finite surface.

Finally apply \autoref{thm:bounded-monotone-cauchy-witness-window-exhaustion} and \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape}. The first rules out a second tail service, and the second rules out escape through limit selection, equality principles, completeness, compactness, or choice-like selection. Thus every completion-facing consumer must pass through the scheduled envelope and the finite apartness-budget rows before the seal row is consumed.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_completion\_consumer\_apartness\_budget}

\begin{theorem}[Bounded monotone Cauchy witness envelope uniqueness]
\label{thm:bounded-monotone-cauchy-witness-envelope-uniqueness}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. If two completion-facing consumer routes for $W$ are admitted before the $\RealUp$ seal row is read, then both routes consume the same scheduled tail envelope rows
$$
S,F,\sigma,\mu,\lambda,I,H,C,P,N
$$
and only then read the seal row $Q$.

Any claimed difference between the two pre-seal envelopes is not a second completion route for $W$. It is routed to the refusal boundary for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selectors.
\end{theorem}
\begin{proof}
First identify the exported envelope. By \autoref{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export}, the only public pre-seal service is the displayed tuple $S,F,\sigma,\mu,\lambda,I,H,C,P,N$.

Next apply completion non-escape. \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape} forces every completion-facing consumer of $W$ through that public envelope, the finite-read route, the regular handoff, the located trap, and the seal row.

The apartness and budget rows are fixed before the seal by \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-apartness-budget}. Thus two admitted routes cannot differ on $\sigma,\mu,\lambda,I$ while remaining completion-facing routes for the same accepted packet.

It remains to rule out a second finite envelope with the same visible role. The finite-observation lock \autoref{thm:bounded-monotone-cauchy-witness-finite-observation-lock} keeps Real-facing finite reads on the displayed rows of $W$, and \autoref{thm:bounded-monotone-cauchy-witness-window-exhaustion} rules out a hidden tail service. Therefore any disagreement is outside the finite envelope and is handled by the existing refusal boundary for the listed non-envelope principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_envelope\_uniqueness}

\begin{theorem}[Bounded monotone Cauchy witness completion observation route]
\label{thm:bounded-monotone-cauchy-witness-completion-observation-route}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every completion-facing observation route for $W$ first consumes the rows
$$
S,F,\sigma,\mu,\lambda,I,H,C,P,N,
$$
then passes through the finite $\RealObservationBudgetUp$ route, the $\RegSeqRatUp$ handoff, the $\LocatedIntervalUp$ trap, and only then reads the $\RealUp$ seal row $Q$.

The route exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector. Thus completion consumers read the finite observation surface before any Real-facing seal is consumed.
\end{theorem}
\begin{proof}
First expose the scheduled envelope. By \autoref{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export}, the public pre-seal rows of $W$ are exactly $S,F,\sigma,\mu,\lambda,I,H,C,P,N$.

Next route the completion consumer through the finite observation surface. Apply \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape} to force the read through the public envelope, the finite observation route, the regular rational handoff, the located trap, and the later seal row.

The apartness and budget rows fix the order of the finite segment. By \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-apartness-budget}, $\sigma,\mu,\lambda,I$ are consumed before the $\RealUp$ seal row $Q$, so the seal cannot precede the finite observation route.

Finally use envelope uniqueness. \autoref{thm:bounded-monotone-cauchy-witness-envelope-uniqueness} rules out a second pre-seal envelope, and the non-escape conclusion excludes selected limits, equality principles, trichotomy, completeness, compactness, and choice-like selectors from the exported route.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_completion\_observation\_route}

\begin{theorem}[Bounded monotone Cauchy witness Real observation seal factorization]
\label{thm:bounded-monotone-cauchy-witness-real-observation-seal-factorization}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every Real-completion-facing consumer of $W$ factors in the following order: first through the scheduled tail envelope
$$
S,F,\sigma,\mu,\lambda,I,H,C,P,N,
$$
then through the finite $\RealObservationBudgetUp$ route, then through the $\RegSeqRatUp$ handoff and $\LocatedIntervalUp$ trap, and only then through the $\RealUp$ seal row $Q$.

Consequently the consumer never receives a selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector. The only public seal-facing dependency surface is the finite package $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ with the pre-seal rows consumed before $Q$.
\end{theorem}
\begin{proof}
Start with the envelope rows. Theorem~\ref{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export} identifies the scheduled tail envelope as the displayed pre-seal service and places $S,F,\sigma,\mu,\lambda,I,H,C,P,N$ before the seal row.

Next apply the completion-consumer non-escape theorem. It forces every Real-completion-facing consumer through the public envelope, the finite observation route, the regular rational handoff, the located trap, and the later $\RealUp$ seal, with no additional completion object exposed.

The pre-seal order is fixed by the apartness-budget theorem. Theorem~\ref{thm:bounded-monotone-cauchy-witness-completion-consumer-apartness-budget} requires the rows $\sigma,\mu,\lambda,I$ to be consumed before the seal row $Q$, so the finite budget cannot be read after the Real seal.

Finally use the completion observation route. Theorem~\ref{thm:bounded-monotone-cauchy-witness-completion-observation-route} binds the observation route to the same envelope, budget, handoff, trap, and seal order. Its non-escape conclusion rules out selected limits, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, and choice-like selectors from the exported surface.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_real\_observation\_seal\_factorization}

\begin{theorem}[Bounded monotone Cauchy witness completion envelope determinacy]
\label{thm:bounded-monotone-cauchy-witness-completion-envelope-determinacy}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. If two completion-facing observation routes for $W$ agree on the scheduled envelope rows
$$
S,F,\sigma,\mu,\lambda,I,H,C,P,N
$$
before the $\RealUp$ seal row $Q$ is read, then they determine the same accepted completion-facing envelope.

The two routes cannot differ by selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector. The only accepted pre-seal completion surface is the displayed scheduled envelope.
\end{theorem}
\begin{proof}
First identify the pre-seal rows. The public export theorem \autoref{thm:bounded-monotone-cauchy-witness-tail-envelope-public-export} presents $S,F,\sigma,\mu,\lambda,I,H,C,P,N$ as the scheduled tail envelope read before $Q$.

Next force both routes through that envelope. By \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape}, any completion-facing observation of $W$ must pass through the public envelope, the finite observation route, the regular handoff, and the located trap before it reaches the seal row.

The finite order is fixed by the apartness-budget theorem. \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-apartness-budget} places $\sigma,\mu,\lambda,I$ before $Q$, so the agreed pre-seal rows cannot be bypassed by a later seal read.

Finally use envelope uniqueness. \autoref{thm:bounded-monotone-cauchy-witness-envelope-uniqueness} rules out a second pre-seal route for the same packet, and \autoref{thm:bounded-monotone-cauchy-witness-completion-observation-route} keeps the completion-facing read on the finite observation surface. Hence the two routes determine the same accepted envelope and cannot differ by any of the excluded completion or equality principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_completion\_envelope\_determinacy}

\begin{corollary}[Bounded monotone Cauchy witness tail envelope strict local obstruction]
\label{cor:bounded-monotone-cauchy-witness-tail-envelope-strict-local-obstruction}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet, and let $E=(S,F,\sigma,\mu,\lambda,I,H,C,P,N)$ be its scheduled tail envelope. Any completion-facing use of the tail envelope factors through the displayed pre-seal rows
$$
S,F,\sigma,\mu,\lambda,I,H,C,P,N,
$$
then through the finite $\RealObservationBudgetUp$ route, the $\RegSeqRatUp$ handoff, the $\LocatedIntervalUp$ trap, and finally the $\RealUp$ seal row $Q$.

Consequently the obstruction carried by the completion-consumer non-escape row is strict and local. It blocks exactly the attempted converse or reuse route that reads the finite tail envelope as a selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, choice-like tail selector, or unlisted validation coordinate. It does not state a global impossibility theorem, does not supply a host-real theorem, and does not certify any external completion principle outside the displayed packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.
\end{corollary}
\begin{proof}
Apply \autoref{thm:bounded-monotone-cauchy-witness-completion-consumer-nonescape}. It sends every completion-facing consumer of $W$ through the public envelope $E$, the finite observation route, the regular rational handoff, the located trap, and the seal row, and it explicitly excludes selected limits, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, and choice-like tail selectors from the consumer surface.

Apply \autoref{thm:bounded-monotone-cauchy-witness-completion-observation-route}. This fixes the order of any completion-facing observation: the rows $S,F,\sigma,\mu,\lambda,I,H,C,P,N$ are consumed before the finite observation route and before the seal row $Q$. Therefore a claimed converse or reuse route must either factor through those rows or ask for a coordinate not exported by the accepted packet.

If the claimed route asks only for the listed rows, it is not obstructed by the non-escape conclusion; it is just the admitted local observation route. If it asks for a selected limit, an equality principle, trichotomy, completeness, compactness, a choice-like selector, or an external validation coordinate, then the request is rejected precisely because that coordinate is absent from the finite dependency surface. The rejection is therefore local to the named converse or reuse attempt.

Nothing in the two cited theorems quantifies over all host real constructions, all completion theorems, or all external validation mechanisms. Their common conclusion is only that the accepted $\BoundedMonotoneCauchyWitnessUp$ packet exposes the displayed finite rows and no additional completion-facing coordinate. Hence the obstruction cannot be reinterpreted as a global impossibility, a host theorem, or a hidden external validation principle.
\end{proof}
