\begin{theorem}[Bounded monotone Cauchy witness root window extraction]\label{thm:bounded-monotone-cauchy-witness-root-window-extraction}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing consumer that reads $W$ for a convergence-seal, limit-seal, or real-seal input first extracts the finite window route
$$
S,F,\sigma,\mu,\lambda
$$
before it reads the located trap $I$, the Real seal row $Q$, or the transport, continuation, provenance, and local naming rows $H,C,P,N$. The extraction is a finite $\BHist$ route through the bounded source, regular rational handoff, stream schedule, Cauchy witness, and dyadic ledger, not an appeal to selected limits, quotient real equality, host real equality, trichotomy, ambient completeness, or open-cover compactness.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:bounded-monotone-cauchy-witness-carrier}. Its root-facing rows are exactly $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, with no hidden coordinate for a limiting representative or ambient completion principle.

Use the local NameCert obligations and scoped dependency package, \autoref{thm:bounded-monotone-cauchy-witness-namecert-obligations} and \autoref{thm:bounded-monotone-cauchy-witness-scoped-dependency-package}. They place source reads in $S$, regular handoff in $F$, stream windows in $\sigma$, Cauchy witnesses in $\mu$, and dyadic ledger data in $\lambda$ before the located and seal rows are available.

Finally apply root extraction and root seal route exhaustion, \autoref{thm:bounded-monotone-cauchy-witness-root-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-seal-route-exhaustion}. Those theorems identify every root consumer with the same finite packet, so the window route $S,F,\sigma,\mu,\lambda$ is the first extracted segment of the route.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_window\_extraction}

\begin{theorem}[Bounded monotone Cauchy witness root window readiness]\label{thm:bounded-monotone-cauchy-witness-root-window-readiness}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing $\RealUp$, $\CauchyLimitSealUp$, or completion-facing seal consumer of $W$ must first read the displayed packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
as its explicit readiness surface. The prefix
$$
S,F,\sigma,\mu,\lambda
$$
is the readiness prefix, and the suffix
$$
I,Q,H,C,P,N
$$
is the seal suffix. The surface exports the bounded source row, regular rational handoff, scheduled window, tail modulus, dyadic ledger, located trap, Real seal row, transport, continuation, provenance, and local naming row, and it exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_window\_readiness}
\begin{proof}
First read the root window extraction row. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} forces every root-facing consumer through $S,F,\sigma,\mu,\lambda$ before any located trap, Real seal, transport, continuation, provenance, or naming suffix is available.

Next read the tail-modulus ledger. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} keeps every tail request on the displayed $\mu,\sigma,\lambda$ ledger, so the readiness prefix is not merely a carrier projection but the public tail-service surface consumed before a seal route can be read.

Now pull the route back to the public criterion-tail boundary. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} identifies any such $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer with the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ packet displayed by $W$.

Finally apply root Real-seal nonescape. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} identifies the remaining rows as exactly $I,Q,H,C,P,N$. The accepted carrier has no coordinate for a selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, so the displayed prefix and suffix together form the whole readiness surface consumed by Real-facing and completion-facing seal routes.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root tail modulus ledger]\label{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing tail request made to $W$ is ledgered by the displayed triple
$$
\mu,\sigma,\lambda
$$
before any located-trap row $I$, Real seal row $Q$, or completion-facing handoff is read. The modulus answer $\mu$, scheduled window $\sigma$, and dyadic ledger $\lambda$ therefore form the public tail-modulus ledger for the root route, and no consumer may replace that ledger by a selected tail, quotient representative, host equality, trichotomy, ambient completeness, or open-cover compactness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_tail\_modulus\_ledger}
\begin{proof}
Start from the carrier and NameCert rows. The carrier makes $\mu,\sigma,\lambda$ displayed components, while the NameCert obligations keep Cauchy-tail, window, and dyadic-budget reads inside those components.

Apply \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction}. It forces the root consumer through $S,F,\sigma,\mu,\lambda$ before $I$ or $Q$, so the tail request is already tied to the scheduled window and dyadic ledger before a trap or seal can be consumed.

Now use the monotone-bound route and the limit-seal handoff, \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route} and \autoref{thm:bounded-monotone-cauchy-witness-limit-seal-handoff}. The bounded monotone source reaches the seal-facing suffix only through the same modulus ledger, and the handoff to $\CauchyLimitSealUp$ and $\RealUp$ preserves that finite route.

The root seal route exhaustion theorem then rules out every alternate tail service. Since the exhausted packet contains no selected tail, quotient representative, host equality, trichotomy, ambient completeness, or compactness row, the displayed triple is the whole public root tail-modulus ledger.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root criterion-tail pullback]\label{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\RealUp$ seal or convergence-seal consumer that uses the ledger triple
$$
\mu,\sigma,\lambda
$$
must factor through the public criterion-tail route of \autoref{thm:bounded-monotone-cauchy-witness-criterion-tail-factorization} before it reads the located-trap row $I$ or the Real-seal row $Q$. The pullback of such a consumer is the finite packet already displayed by the carrier: the $\BHist$ rows, $\hsame$ transports, $\Cont$ continuations, $\Pkg$ provenance, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ row.

Consequently the root route exports no selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\begin{proof}
Start with root window extraction and the root tail modulus ledger. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} place every root-facing read through $S,F,\sigma,\mu,\lambda$ and then through the displayed ledger triple $\mu,\sigma,\lambda$ before any access to $I$ or $Q$.

Next apply the criterion-tail factorization of \autoref{thm:bounded-monotone-cauchy-witness-criterion-tail-factorization}. That factorization is the public route from the bounded monotone source into the Cauchy criterion tail surface, so a consumer using the root ledger cannot jump directly from $\mu,\sigma,\lambda$ to a Real-facing seal read.

Finally use the limit-seal handoff and the root Real-seal nonescape boundary. The handoff keeps the route inside $\CauchyLimitSealUp$ and $\RealUp$ as a displayed BEDC packet, while nonescape identifies the remaining suffix as $I,Q,H,C,P,N$ rather than an unledgered completion object.

The resulting pullback is therefore exactly the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet displayed by the accepted carrier. Since this packet has no coordinate for selected limits, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, none of those objects is available to the root-facing consumer.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_criterion\_tail\_pullback}

\begin{theorem}[Bounded monotone Cauchy witness root Real-seal nonescape]\label{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. The rows $I,Q,H,C,P,N$ hand off only the displayed packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
to $\CauchyLimitSealUp$ and $\RealUp$. This handoff exports the located trap, Real seal route, componentwise transport, continuation, package provenance, and local naming rows, but it exports no selected limit, quotient equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or unledgered completion principle.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_real\_seal\_nonescape}
\begin{proof}
Read the suffix through the accepted carrier. The rows $I,Q,H,C,P,N$ are the located trap, Real seal, transport, continuation, provenance, and naming coordinates of the same finite packet, not a second source of completion data.

Use the root window extraction and tail modulus ledger rows proved above. They force every root-facing request through $S,F,\sigma,\mu,\lambda$ and through the ledger $\mu,\sigma,\lambda$ before any read of $I,Q,H,C,P,N$.

Apply the limit-seal handoff and monotone-bound route, \autoref{thm:bounded-monotone-cauchy-witness-limit-seal-handoff} and \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route}. These identify the $\CauchyLimitSealUp$ and $\RealUp$ consumers with the same bounded-source, regular-handoff, scheduled-tail, located-trap, and seal route.

Finally cite root seal route exhaustion. Once the route is exhausted by $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, no selected limit, quotient equality, host real equality, trichotomy, ambient completeness, compactness, or unledgered completion principle remains for the Real-seal handoff to export.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness window-meet route]
\label{thm:bounded-monotone-cauchy-witness-window-meet-route}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing convergence consumer or Real-seal consumer using the displayed window route must pass through the common finite sequence
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The route composes root window extraction, root tail modulus ledgering, criterion-tail pullback, and root Real-seal nonescape. It exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_meet\_route}
\begin{proof}
Begin with root window extraction. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} forces the root-facing consumer through $S,F,\sigma,\mu,\lambda$ before the located trap or seal suffix can be read.

Next apply the root tail modulus ledger. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} keeps every tail request ledgered by $\mu,\sigma,\lambda$ inside the same finite packet.

Use criterion-tail pullback. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} pulls any Real-facing or convergence-facing consumer back to the public criterion-tail route and its displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Finally apply root Real-seal nonescape. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} identifies the remaining suffix as $I,Q,H,C,P,N$ and excludes every selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, and choice-like tail selector. The carrier of \autoref{def:bounded-monotone-cauchy-witness-carrier} has no alternate coordinate, so the displayed sequence is the whole window-meet route.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root window seal synchronizer]
\label{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\RealUp$ seal or convergence-seal consumer that uses the window route must synchronize the prefix
$$
S,F,\sigma,\mu,\lambda
$$
with the suffix
$$
I,Q,H,C,P,N
$$
through the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ route. The synchronized packet is
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N,
$$
and it exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\begin{proof}
Begin with root window extraction and the root tail modulus ledger. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} place the prefix rows $S,F,\sigma,\mu,\lambda$ and the ledger triple $\mu,\sigma,\lambda$ before any root-facing read of the located trap, Real seal, transport, continuation, provenance, or naming suffix.

Next use the criterion-tail pullback. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} identifies every such Real-facing or convergence-facing consumer with the public criterion-tail route and its displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Apply root Real-seal nonescape and the window-meet route. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} and~\ref{thm:bounded-monotone-cauchy-witness-window-meet-route} identify the suffix as $I,Q,H,C,P,N$ and show that prefix and suffix are consumed as the single finite packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

The accepted carrier has no further coordinate for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection. Hence any root-facing seal consumer using the window route must synchronize through the displayed finite BEDC packet.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_window\_seal\_synchronizer}

\begin{theorem}[Bounded monotone Cauchy witness Real-seal selector exhaustion]
\label{thm:bounded-monotone-cauchy-witness-real-seal-selector-exhaustion}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Any $\RealUp$, $\CauchyLimitSealUp$, or completion-facing consumer that asks for a selector must factor through the displayed prefix
$$
S,F,\sigma,\mu,\lambda
$$
and the displayed suffix
$$
I,Q,H,C,P,N.
$$
After those rows are fixed, the accepted packet has no coordinate for a second selector, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection.
\end{theorem}
\begin{proof}
First expose the selector prefix. Root window extraction and the root tail modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, place every root-facing selector request on $S,F,\sigma,\mu,\lambda$ and on the displayed $\mu,\sigma,\lambda$ tail ledger before any Real seal is read.

Next pull the selector request back to the public tail boundary. The criterion-tail pullback \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} identifies the consumer with the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ route already displayed by the accepted packet.

Then read the seal suffix. Root Real-seal nonescape and the window-meet route, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} and \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route}, identify the remaining rows as exactly $I,Q,H,C,P,N$ and exclude any unshown completion or choice service.

Finally apply the root window seal synchronizer \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}. It binds the prefix and suffix into the single packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so a consumer that asks for selector data has exhausted every selector-facing coordinate before the Real seal is read.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_real\_seal\_selector\_exhaustion}

\begin{theorem}[Bounded monotone Cauchy witness window Real-seal pullback]
\label{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer using the synchronized window factors through the displayed packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The pullback exports the bounded source row, regular rational handoff, scheduled window, tail modulus, dyadic ledger, located trap, Real seal, componentwise transport, continuation, package provenance, and local naming row, and it exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\begin{proof}
Begin with root window extraction. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} forces any root-facing Real or limit-seal consumer to read the prefix $S,F,\sigma,\mu,\lambda$ before it reaches a trap, seal, transport, continuation, provenance, or naming suffix.

Next apply the root tail modulus ledger and criterion-tail pullback. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} and~\ref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} keep the tail request on the displayed $\mu,\sigma,\lambda$ ledger and pull the consumer back through the public criterion-tail route.

Now use root Real-seal nonescape. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} identifies the seal-facing suffix as $I,Q,H,C,P,N$ and rules out every unledgered completion object at that boundary.

Finally apply the window-meet route and root window seal synchronizer. Theorems~\ref{thm:bounded-monotone-cauchy-witness-window-meet-route} and~\ref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer} combine the prefix and suffix into the single finite packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Since the accepted carrier has no further coordinate, every synchronized root-facing Real or limit-seal read factors through exactly that displayed BEDC packet.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_real\_seal\_pullback}

\begin{theorem}[Bounded monotone Cauchy witness window completion pullback]
\label{thm:bounded-monotone-cauchy-witness-window-completion-pullback}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing completion consumer or $\RealUp$-seal consumer using the synchronized window route factors through the finite packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The pullback is completion-facing only through the displayed bounded source row, regular rational handoff, scheduled window, tail modulus, dyadic ledger, located trap, Real seal, componentwise transport, continuation, package provenance, and local naming row. It exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_completion\_pullback}
\begin{proof}
Begin with root window extraction. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-window-extraction} places every root-facing completion read on the displayed prefix $S,F,\sigma,\mu,\lambda$ before the consumer can reach a seal or naming suffix.

Next apply the root tail modulus ledger and criterion-tail pullback. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger} and~\ref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} keep the tail request inside $\mu,\sigma,\lambda$ and route the consumer back to the public criterion-tail packet.

Use root Real-seal nonescape. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape} identifies the seal-facing suffix as $I,Q,H,C,P,N$ and blocks any reading that would replace the displayed rows by an unshown completion object.

Finally compose the window-meet route, root window seal synchronizer, and window Real-seal pullback. Theorems~\ref{thm:bounded-monotone-cauchy-witness-window-meet-route},~\ref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, and~\ref{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback} make the synchronized completion-facing route the single packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Since the accepted carrier contains no coordinate for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, every such consumer factors through exactly the displayed BEDC packet.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness window completion terminality]
\label{thm:bounded-monotone-cauchy-witness-window-completion-terminality}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every completion-facing consumer, $\RealUp$-seal-facing consumer, or convergence-seal-facing consumer that factors through the synchronized window-completion route factors through exactly the displayed packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
This packet is terminal for such consumers: it exposes the bounded source row, regular rational handoff, scheduled window, tail modulus, dyadic ledger, located trap, Real seal, componentwise transport, continuation, package provenance, and local naming row, and it exposes no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, hidden tail selector, or choice-like tail service.
\end{theorem}
\begin{proof}
First extract the finite window route from the root carrier. The root window extraction and root tail modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, force the consumer through $S,F,\sigma,\mu,\lambda$ and through the ledger $\mu,\sigma,\lambda$ before any located trap, Real seal, transport, continuation, provenance, or naming row is read.

Next pull the route back to the public criterion-tail and Real-seal boundaries. Apply criterion-tail pullback, root Real-seal nonescape, and the window-meet route, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback}, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, and \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route}. These identify every completion-facing, Real-seal-facing, or convergence-seal-facing read with the same finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ packet.

Then synchronize the seal suffix with the window prefix. The root window seal synchronizer and window Real-seal pullback, \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer} and \autoref{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback}, make the prefix $S,F,\sigma,\mu,\lambda$ and suffix $I,Q,H,C,P,N$ a single route rather than two independently selectable services.

Finally use the window completion pullback, \autoref{thm:bounded-monotone-cauchy-witness-window-completion-pullback}. It states that every synchronized completion-facing consumer already factors through $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Coordinate exhaustion of the accepted carrier now gives terminality. The carrier of \autoref{def:bounded-monotone-cauchy-witness-carrier} has exactly the displayed coordinates and has no coordinate for a selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, hidden tail selector, or choice-like tail service. Hence all completion-facing consumers of the synchronized route factor through exactly the displayed packet, and there is no further completion-facing datum through which they can factor.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_completion\_terminality}

\begin{theorem}[Bounded monotone Cauchy witness Real-seal modulus determinacy]
\label{thm:bounded-monotone-cauchy-witness-real-seal-modulus-determinacy}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ and $W'=(S',F',\sigma',\mu',\lambda',I',Q',H',C',P',N')$ be accepted $\BoundedMonotoneCauchyWitnessUp$ packets. Suppose the bounded source rows, regular rational handoff rows, scheduled window rows, tail modulus rows, dyadic ledger rows, located trap rows, Real seal rows, $\hsame$ transport rows, $\Cont$ route rows, $\Pkg$ provenance rows, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ rows agree componentwise as displayed carrier coordinates. Then every root-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer that reads either packet reads the same finite Real-seal route
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
and hence the displayed tail-modulus packet uniquely determines the Real-seal readback. The determinacy is internal to the finite carrier route; it does not select a limit, identify quotient reals, assert host equality, use trichotomy, invoke ambient completeness, appeal to open-cover compactness, or install any choice-like tail selector.
\end{theorem}
\begin{proof}
First extract the shared root window. The root window extraction and root tail modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, force both consumers through the componentwise-agreeing rows $S,F,\sigma,\mu,\lambda$ and the same ledger triple $\mu,\sigma,\lambda$ before either consumer can read a located trap or Real seal row.

Next pull the two reads back to the public criterion-tail boundary. The criterion-tail pullback and root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, identify the remaining data as the displayed located trap, Real seal, transport, continuation, provenance, and local naming suffix rather than any unshown completion object.

Now synchronize the suffix with the window route. The window-meet route and root window seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, make the agreeing prefix and agreeing suffix a single finite route for both root-facing consumers.

Finally use the window Real-seal pullback, window completion pullback, and window completion terminality, \autoref{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback}, \autoref{thm:bounded-monotone-cauchy-witness-window-completion-pullback}, and \autoref{thm:bounded-monotone-cauchy-witness-window-completion-terminality}. These theorems leave no completion-facing datum outside the accepted carrier.

Coordinate exhaustion of \autoref{def:bounded-monotone-cauchy-witness-carrier} completes the comparison. Since the two accepted packets agree in every displayed coordinate and the carrier has no coordinate for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, every root-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer reads the same finite Real-seal route from $W$ and $W'$.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_real\_seal\_modulus\_determinacy}

\begin{theorem}[Bounded monotone Cauchy witness monotone-source seal bridge]
\label{thm:bounded-monotone-cauchy-witness-monotone-source-seal-bridge}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet, and let $M=(F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be the accepted $\MonotoneCauchyUp$ monotone source component read by $W$. Every root-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer of $W$ factors first through the monotone-source finite tail-window and cofinality handoff of $M$, then through the bounded-witness root window seal synchronizer for $W$, and finally through the bounded-witness Real-seal modulus determinacy route. The composed bridge is the displayed finite packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N,
$$
with the monotone-source window rows $F,\sigma,\mu,\lambda,I,Q$ read before the bounded source row $S$ is allowed to expose any root-facing seal consumption. The bridge supplies no quotient real equality, selected representative, trichotomy, open-cover compactness, ambient completeness, host real equality, or choice-like tail selector.
\end{theorem}
\begin{proof}
First read the monotone source through $M$. Theorem~\ref{thm:monotone-cauchy-window-tail-cofinality-handoff} forces any $\RealUp$ seal consumer using the monotone Cauchy source and a cofinal tail schedule through $F,\sigma,\mu,\lambda,I,Q$ before the seal row is readable, and it excludes quotient equality, selected representatives, host real order, ambient completeness, open-cover compactness, and choice.

Next attach the bounded-witness root row. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer} synchronizes the bounded source prefix $S,F,\sigma,\mu,\lambda$ with the seal suffix $I,Q,H,C,P,N$ as one finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ route.

Finally apply \autoref{thm:bounded-monotone-cauchy-witness-real-seal-modulus-determinacy}. Once the monotone-source handoff and bounded-witness synchronizer have displayed the same rows, the tail-modulus packet uniquely determines the root-facing Real-seal readback. The accepted packets contain no additional coordinate for quotient real equality, selected representatives, trichotomy, open-cover compactness, ambient completeness, host real equality, or choice-like tail selection, so every root-facing $\RealUp$ or $\CauchyLimitSealUp$ consumer factors through exactly the composed finite bridge.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_monotone\_source\_seal\_bridge}

\begin{theorem}[Bounded monotone Cauchy witness window seal completeness]
\label{thm:bounded-monotone-cauchy-witness-window-seal-completeness}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing $\RealUp$ consumer, root-facing $\CauchyLimitSealUp$ consumer, or completion consumer that uses the synchronized window route factors through exactly the finite packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
Conversely, every displayed window-seal read of that packet supplies the whole readiness surface for those consumers: bounded source, regular rational handoff, scheduled window, tail modulus, dyadic ledger, located trap, Real seal, componentwise $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ naming row. No selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, hidden tail selector, or choice-like tail service is part of the readiness surface.
\end{theorem}
\begin{proof}
First build the finite route. The window-meet route and root window seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, identify the root window prefix $S,F,\sigma,\mu,\lambda$ with the seal suffix $I,Q,H,C,P,N$ as one packet.

Next pass to the Real and completion boundaries. The window Real-seal pullback and window completion pullback, \autoref{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-window-completion-pullback}, make every root-facing $\RealUp$, root-facing $\CauchyLimitSealUp$, and completion read factor through that synchronized packet.

Then use terminality. By \autoref{thm:bounded-monotone-cauchy-witness-window-completion-terminality}, the displayed coordinates are the terminal readiness packet for completion-facing and seal-facing consumers, so no consumer can require data outside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Finally apply Real-seal modulus determinacy, \autoref{thm:bounded-monotone-cauchy-witness-real-seal-modulus-determinacy}. It states that componentwise agreement of the displayed packet determines the root-facing Real-seal readback, which gives the converse: reading the displayed window-seal packet supplies exactly the readiness surface used by the Real, limit-seal, and completion consumers.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_seal\_completeness}

\begin{theorem}[Bounded monotone Cauchy witness window readback stability]
\label{thm:bounded-monotone-cauchy-witness-window-readback-stability}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ and $W'=(S',F',\sigma',\mu',\lambda',I',Q',H',C',P',N')$ be accepted $\BoundedMonotoneCauchyWitnessUp$ packets. Suppose the displayed rows $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ are preserved componentwise by $\hsame$ and that both packets replay the same displayed $\Cont$ window-seal route. Then every root-facing $\RealUp$, $\CauchyLimitSealUp$, or completion consumer reads the same window-seal readiness surface from $W$ and $W'$. The stability claim uses only the finite window-meet route, root window seal synchronizer, window Real-seal pullback, window completion pullback, terminality, and Real-seal modulus determinacy; it does not select limits, identify quotient reals, assert host equality, use trichotomy, invoke ambient completeness, appeal to open-cover compactness, or install choice-like tail services.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_readback\_stability}
\begin{proof}
First compose the shared window route. The window-meet route and root window seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, force both packets through the same displayed prefix and suffix under the assumed componentwise $\hsame$ transport and $\Cont$ replay.

Next pull the read to the Real and completion boundaries. The window Real-seal pullback and window completion pullback, \autoref{thm:bounded-monotone-cauchy-witness-window-real-seal-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-window-completion-pullback}, make every root-facing $\RealUp$, $\CauchyLimitSealUp$, and completion consumer factor through the finite packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Finally apply terminality and Real-seal modulus determinacy. Theorem~\ref{thm:bounded-monotone-cauchy-witness-window-completion-terminality} leaves no completion-facing datum outside the displayed carrier, and Theorem~\ref{thm:bounded-monotone-cauchy-witness-real-seal-modulus-determinacy} makes the componentwise-preserved window packet determine the Real-seal readback. The carrier has no coordinate for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail services, so the readiness surface read from $W$ and $W'$ is the same.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness CauchyCriterion selector handoff]
\label{thm:bounded-monotone-cauchy-witness-cauchycriterion-selector-handoff}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet, and let $K=(W_K,M,T,Q_K,E,H_K,C_K,P_K,N_K)$ be an accepted $\CauchyCriterionUp$ packet. Suppose the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows displayed by the two packets agree at the selector-seal boundary. Then every $\RealUp$-facing, $\CauchyLimitSealUp$-facing, or completion-facing read of the bounded monotone window-seal packet factors through the same finite $\CauchyCriterionUp$ budget-selector surface
$$
M,\quad Q_K,\quad T,\quad W_K,\quad E,\quad H_K,\quad C_K,\quad P_K,\quad N_K
$$
before any $\RealUp$ seal is exposed. The handoff uses only the shared StreamName--RegSeqRat--DyadicRatCore--Real rows and the finite support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$; it does not introduce quotient streams, selected limits, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selectors.
\end{theorem}
\begin{proof}
First close the bounded monotone window packet. The window seal completeness and window readback stability theorems, \autoref{thm:bounded-monotone-cauchy-witness-window-seal-completeness} and \autoref{thm:bounded-monotone-cauchy-witness-window-readback-stability}, put every $\RealUp$-facing, $\CauchyLimitSealUp$-facing, and completion-facing read of $W$ on the displayed finite packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Next expose the selector surface. The CauchyCriterion StreamName Real budget-selector boundary, \autoref{thm:cauchycriterion-streamname-real-budget-selector-boundary}, makes every consumer sharing the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows read through $M,Q_K,T,W_K,E,H_K,C_K,P_K,N_K$ before selector output is exposed.

Then use uniform selector-seal compatibility, \autoref{thm:cauchycriterion-uniform-selector-seal-compatibility}. It records that the selector-facing CauchyCriterion route and any matching seal route factor through the same finite StreamName--RegSeqRat--DyadicRatCore--Real surface with the support rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Finally match the shared boundary rows. By hypothesis the bounded monotone packet and the CauchyCriterion packet display the same four public rows at the selector-seal boundary, so the terminal window-seal read of $W$ must pass through the CauchyCriterion budget-selector packet before a $\RealUp$ seal is exposed. Neither accepted carrier has an extra completion coordinate, and the listed exclusions have no displayed row in either packet.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_cauchycriterion\_selector\_handoff}

\begin{theorem}[Bounded monotone Cauchy witness window-seal readback completeness]
\label{thm:bounded-monotone-cauchy-witness-window-seal-readback-completeness}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. A current Phase Real or Completion readback through $\RealUp$, $\CauchyLimitSealUp$, or any completion-facing seal is complete exactly when it exposes the bounded source row $S$, regular rational handoff $F$, scheduled window $\sigma,\lambda$, tail modulus $\mu$, dyadic ledger, located trap $I$, Real seal $Q$, componentwise $\hsame$ transports $H$, displayed $\Cont$ routes $C$, $\Pkg$ provenance $P$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ row $N$. Conversely, any accepted packet exposing those rows supplies the whole readback surface for the bounded monotone witness window. The statement excludes selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, and choice-like tail selection.
\end{theorem}
\begin{proof}
First expose the bounded source prefix. The root window extraction and root tail modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, place every Phase Real or Completion read on $S,F,\sigma,\mu,\lambda$ and the dyadic tail ledger before a trap, seal, transport, route, provenance, or naming row can be read.

Next pull the readback to the public seal boundary. The criterion-tail pullback and root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, identify the remaining surface as $I,Q,H,C,P,N$ rather than a selected limit or host completion object.

The route is then synchronized as one finite packet. Apply the window-meet route and root window seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, to bind the source prefix, tail ledger, located trap, Real seal, transports, continuations, provenance, and local name into the same displayed $\BHist$ packet.

For the forward direction, window completion terminality and Real-seal modulus determinacy, \autoref{thm:bounded-monotone-cauchy-witness-window-completion-terminality} and \autoref{thm:bounded-monotone-cauchy-witness-real-seal-modulus-determinacy}, leave no completion-facing or Real-facing coordinate outside the displayed rows. Thus a complete $\RealUp$, $\CauchyLimitSealUp$, or completion-facing read must expose exactly the listed surface.

For the converse, start from an accepted packet exposing all listed rows. The CauchyCriterion selector handoff, \autoref{thm:bounded-monotone-cauchy-witness-cauchycriterion-selector-handoff}, supplies the selector-facing budget route before any Real seal is exposed, while the synchronized window packet supplies the completion-facing suffix. Since the carrier contains no row for selected limits, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, these rows supply the whole readback surface.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_seal\_readback\_completeness}

\begin{theorem}[Bounded monotone Cauchy witness root window terminal factorization]
\label{thm:bounded-monotone-cauchy-witness-root-window-terminal-factorization}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every root-facing $\RealUp$, $\CauchyLimitSealUp$, or completion consumer of $W$ factors through the single displayed root-window route
$$
S,\quad F,\quad \sigma,\quad \mu,\quad \lambda,\quad I,\quad Q,\quad H,\quad C,\quad P,\quad N.
$$
This route is the only completion-facing factorization surface for the accepted packet: any consumer preserving the bounded source, regular rational handoff, scheduled root window, tail modulus ledger, located trap, Real seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ row preserves the same root-window readback. No selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector is part of the factorization.
\end{theorem}
\begin{proof}
First build the root-window spine. Root window extraction and the root tail modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, put every root-facing read on the displayed bounded source, rational handoff, scheduled window, and tail modulus rows.

Next pull the spine to the public seal boundary. Criterion-tail pullback and root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, force the located trap, Real seal, componentwise transports, continuation replay, provenance, and local naming row to remain attached to that same root route.

Finally close the completion-facing side. Window completion terminality, \autoref{thm:bounded-monotone-cauchy-witness-window-completion-terminality}, says a completion consumer has no further route outside the displayed packet, and window-seal readback completeness, \autoref{thm:bounded-monotone-cauchy-witness-window-seal-readback-completeness}, identifies the whole exposed surface as $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Therefore every root-facing $\RealUp$, $\CauchyLimitSealUp$, or completion consumer factors through exactly this route, and the excluded objects have no carrier coordinate through which a second factorization could pass.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_window\_terminal\_factorization}

\begin{theorem}[Bounded monotone Cauchy witness finite-window factorization package]
\label{thm:bounded-monotone-cauchy-witness-window-factorization}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every $\RealUp$-facing or completion-facing read of $W$ factors through the finite prefix
$$
S,\quad F,\quad \sigma,\quad \mu,\quad \lambda
$$
and then through the finite suffix
$$
I,\quad Q,\quad H,\quad C,\quad P,\quad N.
$$
The prefix records the bounded source, regular rational handoff, scheduled root window, tail modulus ledger, and window selector. The suffix records the located trap, Real seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ row. Thus any $\RealUp$, $\CauchyLimitSealUp$, RegSeqRat, StreamName, or completion-seal consumer preserving these eleven rows reads the same finite window package.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_window\_factorization}
\begin{proof}
First isolate the prefix. Root window extraction and the root tail-modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, place every source-facing and tail-facing read on $S,F,\sigma,\mu,\lambda$ before a located trap or Real seal can be exposed.

Next bind the suffix to that same prefix. Criterion-tail pullback and root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback} and \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, keep the trap, seal, transport, continuation, provenance, and local naming rows attached to the displayed root window.

The window-meet route and root window seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, identify the two halves as one finite $\BHist$ packet. The terminal factorization theorem, \autoref{thm:bounded-monotone-cauchy-witness-root-window-terminal-factorization}, then rules out any further completion-facing route outside these eleven rows.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness Real-seal route]
\label{thm:bounded-monotone-cauchy-witness-real-seal-route}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. The $\RealUp$ seal of $W$ is readable only through the displayed finite route
$$
\BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert_{\BoundedMonotoneCauchyWitnessUp}
$$
carried by $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. This route excludes quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, and choice-like tail selection. In particular, a Real-seal consumer receives the finite BHist row, the componentwise hsame transports, the Cont replay, the Pkg provenance row, and the local NameCert row, and receives no additional real-completion witness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_real\_seal\_route}
\begin{proof}
Start from root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}. It says the Real-facing row cannot leave the finite root-window packet for a selected limit, a host equality judgment, or an ambient completion object.

The window-meet route and window-seal synchronizer, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-seal-synchronizer}, then display the seal route as the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support carried by $W$.

Finally use terminal factorization, \autoref{thm:bounded-monotone-cauchy-witness-root-window-terminal-factorization}. Since the accepted packet has no coordinate for quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection, no Real-seal route can factor through those objects.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness modulus ledger exhaustion]
\label{thm:bounded-monotone-cauchy-witness-modulus-ledger-exhaustion}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. The modulus ledger $\mu,\sigma,\lambda$ is exhausted before either located-trap row $I$ or Real-seal row $Q$ is readable. Equivalently, every located-trap, Real-seal, $\CauchyLimitSealUp$, or completion-facing read first passes through the scheduled window and tail-modulus budget, and only then reaches $I,Q,H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_modulus\_ledger\_exhaustion}
\begin{proof}
The root tail-modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}, records the selector and modulus rows $\sigma,\mu,\lambda$ as the finite budget consumed by the root window. Thus a trap or seal row cannot be read before that budget is displayed.

Criterion-tail pullback, \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback}, transports any criterion-facing tail read back to the same budget rows. Root Real-seal nonescape, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, keeps the Real-seal side on the finite packet rather than on a selected limit or ambient completion object.

The finite-window factorization package above and the terminal factorization theorem, \autoref{thm:bounded-monotone-cauchy-witness-window-factorization} and \autoref{thm:bounded-monotone-cauchy-witness-root-window-terminal-factorization}, identify every downstream read as a prefix read through $S,F,\sigma,\mu,\lambda$ followed by a suffix read through $I,Q,H,C,P,N$. Hence the modulus ledger is exhausted before the located-trap and seal rows are readable.
\end{proof}

\begin{corollary}[Bounded monotone Cauchy witness root-window extraction strict local obstruction]
\label{cor:bounded-monotone-cauchy-witness-root-window-strict-obstruction}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Suppose a displayed failure, refusal, separation, or countermodel row in the root-window extraction, tail-modulus ledger, or Real-seal handoff surface of $W$ is cited against a named converse or reuse route. Then the row is a strict local obstruction: it blocks only the named route whose consumer-facing read tries to omit, replace, detach, or bypass one of the displayed packet coordinates
$$
S,\quad F,\quad \sigma,\quad \mu,\quad \lambda,\quad I,\quad Q,\quad H,\quad C,\quad P,\quad N.
$$
Equivalently, every permitted consumer-facing use of the row factors through the finite root-window prefix
$$
S,F,\sigma,\mu,\lambda
$$
and the seal suffix
$$
I,Q,H,C,P,N,
$$
with support only from the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ rows. The same row cannot be reinterpreted as a global impossibility theorem for $\BoundedMonotoneCauchyWitnessUp$, a host theorem about real completion or monotone convergence, hidden external validation of the failed route, a selected limit, quotient real equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or a choice-like tail selector.
\end{corollary}
\begin{proof}
Start with root-window extraction. By \autoref{thm:bounded-monotone-cauchy-witness-root-window-extraction}, every root-facing convergence-seal, limit-seal, or Real-seal consumer first reads the finite prefix $S,F,\sigma,\mu,\lambda$ before it reaches the located trap, the Real seal, transport, continuation, provenance, or naming rows. Thus a displayed negative row attached to the extraction surface has a named input coordinate inside that prefix; it is not a statement about arbitrary bounded monotone witnesses or arbitrary completion procedures.

Next use the tail-modulus ledger, \autoref{thm:bounded-monotone-cauchy-witness-root-tail-modulus-ledger}. Any root-facing tail request is ledgered by $\mu,\sigma,\lambda$ before $I$, $Q$, or any completion-facing handoff is read. Hence a converse or reuse route that tries to replace the scheduled window, tail modulus, or dyadic ledger by a selected tail, an unledgered completion object, or a choice-like selector has no admitted coordinate. The obstruction blocks precisely that attempted replacement of the displayed ledger and does not acquire wider force.

Now pass to the seal boundary. The root Real-seal nonescape theorem, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-nonescape}, identifies the remaining suffix as exactly $I,Q,H,C,P,N$: the located trap, Real seal route, componentwise transport, continuation, package provenance, and local naming rows. It also says that the handoff to $\CauchyLimitSealUp$ and $\RealUp$ exports no selected limit, quotient equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or unledgered completion principle.

The consumer-facing factorization is therefore finite. By \autoref{thm:bounded-monotone-cauchy-witness-root-criterion-tail-pullback}, \autoref{thm:bounded-monotone-cauchy-witness-window-meet-route}, and \autoref{thm:bounded-monotone-cauchy-witness-root-window-terminal-factorization}, any admitted Real-facing, limit-seal-facing, or completion-facing use of the root window is pulled back to the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ packet carried by $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

It remains to exclude stronger readings. A global impossibility theorem would require a conclusion not indexed by the accepted packet $W$ and not confined to the named failed route. A host theorem would require a host-facing real-completion, monotone-convergence, equality, or compactness coordinate outside the packet. Hidden external validation would require an extra certificate channel beyond $P$, $N$, and the displayed continuation and transport rows. A selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector would require one of the coordinates explicitly absent from the extraction, ledger, and nonescape theorems. Since the accepted carrier exposes none of those coordinates, the displayed row blocks only the named local converse or reuse route and rejects every unlisted interpretation.
\end{proof}
