\begin{theorem}[Bounded monotone Cauchy witness source-row exhaustion]
\label{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}
For an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N),
$$
the bounded monotone source row, regular rational handoff, stream schedule, Cauchy modulus, dyadic ledger, located trap, and $\RealUp$ seal precursor exhaust the witness source surface. Every source-facing read is one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, with no additional range over host real histories, selected limit, quotient equality, trichotomy row, ambient completeness witness, or open-cover compactness row.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_source\_row\_exhaustion}
\begin{proof}
Project the carrier surface of \autoref{def:bounded-monotone-cauchy-witness-carrier}. Its rows list the bounded source, regular rational handoff, stream schedule, Cauchy witness, dyadic ledger, located trap, Real seal precursor, componentwise transport, continuation route, package provenance, and local name.

Apply the local NameCert and scoped-dependency packages, \autoref{thm:bounded-monotone-cauchy-witness-namecert-obligations} and \autoref{thm:bounded-monotone-cauchy-witness-scoped-dependency-package}. These force generator reads through $S$, tail requests through $\mu,\sigma,\lambda$, located enclosures through $I$, classifier transport through $H,C$, and provenance and naming through $P,N$.

The child certificate-surface theorems then close the source boundary. Generator range exactness, tail modulus scope, Real seal boundary, and ledger exhaustion leave no carrier coordinate outside the displayed witness package, so the listed rows exhaust the source surface.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness tail-window lock]
\label{thm:bounded-monotone-cauchy-witness-tail-window-lock}
Every tail-window read exported by an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier factors through $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$ before any $\RealUp$ seal row is read. The tail-window route is therefore the public monotone Cauchy source together with the regular rational tail handoff, not a direct jump from bounded monotonicity to a real-seal coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_tail\_window\_lock}
\begin{proof}
Start from the dependency paragraphs of this chapter. They place $\BoundedMonotoneCauchyWitnessUp$ as the bounded-monotone consumer of \autoref{ch:concrete-instances-monotonecauchy-namecert} and the shared finite tail route of \autoref{ch:concrete-instances-regular-cauchy-tail-meet-namecert}.

Use the scoped-dependency package and the root extraction route. The displayed witness first exposes $S,F,\sigma,\mu,\lambda$ as the monotone source, regular handoff, schedule, Cauchy witness, and dyadic ledger before the located trap and Real seal suffix can be consumed.

Finally apply the convergence-seal source and input-package theorems already input by this chapter. They identify the downstream seal source with the same public monotone Cauchy and regular-tail rows, so a Real-facing consumer cannot read $Q$ before the MonotoneCauchy and RegularCauchyTailMeet routes have been displayed.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness convergence-seal input totality]
\label{thm:bounded-monotone-cauchy-witness-convergence-seal-input-totality}
The $\BoundedMonotoneConvergenceSealUp$ consumer of \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert} consumes exactly the displayed witness package
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
from an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. It receives no selected limit, quotient equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or alternate tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_convergence\_seal\_input\_totality}
\begin{proof}
Read the downstream dependency paragraph together with the scoped-dependency package. The convergence seal asks for a finite monotone source, regular rational handoff, stream schedule, Cauchy modulus, dyadic ledger, located trap, Real seal precursor, and the structural rows carrying transport, continuation, provenance, and naming.

Apply \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-package}. It states that every downstream convergence-seal input exported by $W$ factors through precisely the displayed witness rows before the seal chapter reads it.

The completion-route exhaustion and Real-seal public route exhaustion theorems rule out bypasses. Since selected limits, quotient equality, host equality, trichotomy, ambient completeness, open-cover compactness, and alternate tail selectors are absent from the witness carrier and from the downstream route, the displayed package is total for the convergence-seal input.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness convergence-seal route determinacy]
\label{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy}
For an accepted $\BoundedMonotoneCauchyWitnessUp$ packet
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N),
$$
there is exactly one public convergence-seal route determined by its source, tail, and seal rows. The route first reads the $\MonotoneCauchyUp$ source and the $\RegularCauchyTailMeetUp$ tail window, then passes through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and finally $\RealUp$. A consumer-visible convergence-seal route for $W$ cannot skip any one of those rows, nor can it replace them by selected limits, quotient equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or an alternate tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_convergence\_seal\_route\_determinacy}
\begin{proof}
Start with source-row exhaustion. By \autoref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}, every source-facing read of $W$ is one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so the convergence-seal route has no second source socket.

Next use the tail-window lock. It forces every tail-window read through the public $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$ surfaces before the $\RealUp$ seal row is available.

Now attach convergence-seal input totality. The theorem \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-totality} says that the $\BoundedMonotoneConvergenceSealUp$ consumer receives exactly the displayed witness package. Together with \autoref{thm:bounded-monotone-witness-monotone-cauchy-criterion-bridge} and \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-package}, this inserts the $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ rows in the displayed order.

It remains to rule out alternate public routes. The completion-route exhaustion theorem \autoref{thm:bounded-monotone-cauchy-witness-completion-route-exhaustion} and ledger exhaustion in \autoref{thm:bounded-monotone-cauchy-witness-ledger-exhaustion} leave no consumer-visible coordinate outside the named rows. Any route omitting one of them therefore fails to be a convergence-seal route exported by the accepted packet $W$.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness tail Real-seal route totality]
\label{thm:bounded-monotone-cauchy-witness-tail-real-seal-route-totality}
For an accepted $\BoundedMonotoneCauchyWitnessUp$ packet
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N),
$$
every $\RealUp$-seal consumer of $W$ passes through the source row, the $\MonotoneCauchyUp$ tail source, the $\RegularCauchyTailMeetUp$ window, $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and the final $\RealUp$ row. No such consumer may replace this route by a selected limit, quotient equality, host real equality, trichotomy, open-cover compactness, or alternate tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_tail\_real\_seal\_route\_totality}
\begin{proof}
Begin with source-row exhaustion. The theorem \autoref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion} identifies every source-facing read of $W$ with one of the displayed coordinates $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Next apply the tail-window lock. By \autoref{thm:bounded-monotone-cauchy-witness-tail-window-lock}, a Real-facing tail read must first expose the $\MonotoneCauchyUp$ source and the $\RegularCauchyTailMeetUp$ window, so the tail surface cannot be selected outside the displayed packet.

Now use convergence-seal input totality and route determinacy. Theorems \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-totality} and \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} force the downstream seal route through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ in the named order.

It remains to exhaust the visible coordinates of the route. The source theorem accounts for the displayed $\BHist$ rows, the tail and seal theorems account for the $\hsame$ and $\Cont$ rows, and the local package and certificate rows provide exactly the $\Pkg$ and $\NameCert$ witnesses attached to $P$ and $N$. Since the carrier contains no coordinate for a selected limit, quotient equality, host real equality, trichotomy, open-cover compactness, or alternate tail selector, none of those objects can serve as a Real-seal route for $W$.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness tail seal row determinacy]
\label{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Suppose two downstream convergence-seal reads preserve the same source row $S$, the same public $\MonotoneCauchyUp$ tail source, the same $\RegularCauchyTailMeetUp$ window, the same $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and the same structural rows $H,C,P,N$. Then the two reads determine the same visible $\RealUp$ seal row $Q$.

Equivalently, the displayed tail route fixes the downstream seal row: no accepted read preserving those rows may replace $Q$ by a selected limit, quotient equality, host real equality, trichotomy branch, open-cover compactness witness, ambient completeness object, or alternate tail selector.
\end{theorem}
\begin{proof}
First use source-row exhaustion. By \autoref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}, every source-facing coordinate of $W$ is one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Thus two reads preserving the same source row cannot choose a second source socket from outside the displayed packet.

Next apply the tail-window lock and route determinacy. The tail-window lock forces both reads through the same public $\MonotoneCauchyUp$ source and the same $\RegularCauchyTailMeetUp$ window, while \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} fixes the sibling route through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$.

Finally use the Real-seal route totality. The terminal $\RealUp$ read is a carrier coordinate of the same accepted packet, and the structural rows $H,C,P,N$ are preserved by hypothesis. The coordinate exhaustion in \autoref{thm:bounded-monotone-cauchy-witness-tail-real-seal-route-totality} leaves $Q$ as the only visible terminal seal row and excludes selected limits, quotient equality, host real equality, trichotomy, open-cover compactness, ambient completeness, and alternate tail selectors.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_tail\_seal\_row\_determinacy}

\begin{theorem}[Bounded monotone Cauchy witness Cauchy-ledger readback exactness]
\label{thm:bounded-monotone-cauchy-witness-cauchy-ledger-readback-exactness}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Any $\CauchyWitnessLedgerUp$ readback that consumes the bounded monotone witness factors through the same $\MonotoneCauchyUp$, $\RegularCauchyTailMeetUp$, $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ route fixed by \autoref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy}. Such a readback cannot introduce a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, or alternate completion route.
\end{theorem}
\begin{proof}
First read the source surface. By \autoref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}, every source-facing coordinate available to the ledger is one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Next lock the tail and seal route. The tail-window theorem forces the read through $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$, while convergence-seal input totality and route determinacy insert $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ in the displayed order.

Finally apply tail seal row determinacy. Once the ledger preserves the same source, tail, seal, transport, route, provenance, and naming rows, the visible $\RealUp$ seal row is fixed as $Q$. Coordinate exhaustion leaves no socket for a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, or alternate completion route, so the ledger readback is exact.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_cauchy\_ledger\_readback\_exactness}

\begin{theorem}[Bounded monotone Cauchy witness criterion-ledger route totality]
\label{thm:bounded-monotone-cauchy-witness-criterion-ledger-route-totality}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every $\CauchyCriterionUp$ consumer or $\CauchyWitnessLedgerUp$ consumer that reads the bounded monotone witness factors through the same route fixed by \autoref{thm:bounded-monotone-cauchy-witness-cauchy-ledger-readback-exactness}: the $\MonotoneCauchyUp$ source, the $\RegularCauchyTailMeetUp$ tail window, $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$, together with the structural rows $H,C,P,N$.

Consequently the criterion-ledger route for $W$ is total on the displayed packet coordinates. It has no selected limit, quotient stream equality, host real equality, choice row, hidden tail oracle, ambient completeness object, open-cover compactness row, or alternate completion route.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_criterion\_ledger\_route\_totality}
\begin{proof}
Start with source-row exhaustion. Theorem~\ref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion} identifies every source-facing read of $W$ with one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so a criterion or ledger consumer has no carrier coordinate outside the displayed packet.

Next lock the tail window. Theorem~\ref{thm:bounded-monotone-cauchy-witness-tail-window-lock} routes every tail-facing read through $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$ before any terminal $\RealUp$ seal row is available.

Now use convergence-seal route determinacy and tail seal row determinacy. Theorems~\ref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} and~\ref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy} fix the passage through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$, and they fix the visible seal row once $H,C,P,N$ are preserved.

Finally apply the Cauchy-ledger readback exactness theorem. The readback theorem identifies the ledger-facing route with the same displayed route, while the preceding coordinate exhaustion accounts for all rows of $W$. There is therefore no remaining socket for a selected limit, quotient stream equality, host real equality, choice row, hidden tail oracle, ambient completeness object, open-cover compactness row, or alternate completion route.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness selector-free Real route]
\label{thm:bounded-monotone-cauchy-witness-selector-free-real-route}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every $\RealUp$-facing route through the bounded monotone witness is exhausted by the displayed source row, the $\MonotoneCauchyUp$ tail source, the $\RegularCauchyTailMeetUp$ tail window, $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealUp$, and the structural rows $H,C,P,N$. No such route can introduce a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, or alternate completion route.
\end{theorem}
\begin{proof}
Start with source-row exhaustion. Theorem~\ref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion} identifies every source-facing read of $W$ with one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so a Real-facing consumer has no second carrier surface outside the displayed packet.

Next apply the tail-window lock. Theorem~\ref{thm:bounded-monotone-cauchy-witness-tail-window-lock} routes each tail-facing read through $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$ before any terminal $\RealUp$ row can be read.

Now use convergence-seal route determinacy. Theorem~\ref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} fixes the sibling chain through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ in that order.

Then apply tail seal row determinacy. Theorem~\ref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy} fixes the visible $\RealUp$ seal row once the same source, tail, seal, transport, continuation, provenance, and naming rows are preserved.

Finally use Cauchy-ledger readback exactness. Theorem~\ref{thm:bounded-monotone-cauchy-witness-cauchy-ledger-readback-exactness} identifies the ledger-facing route with the same displayed route, and \autoref{thm:bounded-monotone-cauchy-witness-criterion-ledger-route-totality} accounts for the criterion side. The named source, tail, seal, and structural rows therefore exhaust the Real handoff, leaving no socket for a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, or alternate completion route.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_selector\_free\_real\_route}

\begin{theorem}[Bounded monotone Cauchy witness dyadic-radius budget preservation]
\label{thm:bounded-monotone-cauchy-witness-dyadic-radius-budget-preservation}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every $\RealUp$-facing route preserving the bounded monotone source $S$ and the regular tail rows $\sigma,\mu,\lambda$ also preserves the dyadic radius budget through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and the final $\RealUp$ seal row $Q$. Such a route cannot replace that budget by a selected limit, host real equality, quotient equality, trichotomy branch, open-cover compactness row, or alternate completion route.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_dyadic\_radius\_budget\_preservation}
\begin{proof}
Start with source-row exhaustion. Theorem~\ref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion} confines every source-facing read to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so preservation of $S$ and the regular tail rows already fixes the carrier surface on which the dyadic budget can be read.

Next apply the tail-window lock. Theorem~\ref{thm:bounded-monotone-cauchy-witness-tail-window-lock} routes the preserved tail data through $\MonotoneCauchyUp$ and $\RegularCauchyTailMeetUp$ before a $\RealUp$-facing read can reach the terminal seal.

Use convergence-seal route determinacy and tail seal row determinacy. Theorems~\ref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} and~\ref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy} fix the passage through $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$, and they fix the visible seal row $Q$ once the source, tail, transport, continuation, provenance, and naming rows are preserved.

Finally apply the selector-free Real route. Theorem~\ref{thm:bounded-monotone-cauchy-witness-selector-free-real-route} exhausts every $\RealUp$-facing route by the same displayed source, tail, dyadic, regular-sequence, limit-seal, Real-seal, and structural rows. Coordinate exhaustion therefore leaves no route on which a selected limit, host real equality, quotient equality, trichotomy branch, open-cover compactness row, or alternate completion route could replace the dyadic radius budget.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root tail-budget exactness]
\label{thm:bounded-monotone-cauchy-witness-root-tail-budget-exactness}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Every accepted root-source tail-seal read of $W$ factors through the displayed $\CauchyModulusUp$, $\CauchyModulusExtractionUp$, $\CauchySealBudgetSynchronizerUp$, $\CauchyWitnessLedgerUp$, $\LocatedIntervalUp$, $\MonotoneCauchyUp$, $\RealCauchyWitnessGridUp$, $\RealObservationBudgetUp$, $\RegSeqRatUp$, $\RegularCauchyTailMeetUp$, and $\StreamNameUp$ rows before any $\RealUp$ or completion-facing endpoint is public.

Thus the monotone witness rows determine the same finite L10 tail-budget chain as the root source rows: no accepted read may replace that chain by a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, open-cover compactness row, or alternate completion route.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_tail\_budget\_exactness}
\begin{proof}
Start with the local source rows. Theorems~\ref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}, \ref{thm:bounded-monotone-cauchy-witness-tail-window-lock}, and~\ref{thm:bounded-monotone-cauchy-witness-dyadic-radius-budget-preservation} bind the source row $S$, regular handoff $F$, scheduled windows $\sigma$, Cauchy modulus $\mu$, dyadic ledger $\lambda$, located trap $I$, and Real seal row $Q$ to one displayed packet.

Next read the witness and criterion ledgers. Theorems~\ref{thm:bounded-monotone-cauchy-witness-cauchy-ledger-readback-exactness} and~\ref{thm:bounded-monotone-cauchy-witness-criterion-ledger-route-totality} force every $\CauchyWitnessLedgerUp$ or $\CauchyCriterionUp$ consumer through the same $\MonotoneCauchyUp$, $\RegularCauchyTailMeetUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ route.

Now attach the root sibling routes listed by the chapter. The root unblock and tail-service rows identify the $\CauchyModulusExtractionUp$ schedule, $\CauchySealBudgetSynchronizerUp$ synchronizer, $\RealObservationBudgetUp$ finite observation route, and $\RealCauchyWitnessGridUp$ handoff as consumers of the same source, tail, trap, seal, transport, continuation, provenance, and local naming rows $H,C,P,N$.

Finally apply selector-free Real-route exhaustion. Theorem~\ref{thm:bounded-monotone-cauchy-witness-selector-free-real-route} leaves no endpoint coordinate outside the displayed source, tail, ledger, limit-seal, Real-seal, and structural rows. Therefore any root-source tail-seal read reaches $\RealUp$ or a completion-facing endpoint only after traversing the stated finite tail-budget chain.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness convergence-grid fork coherence]
\label{thm:bounded-monotone-cauchy-witness-convergence-grid-fork-coherence}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Suppose one downstream read consumes $W$ through $\BoundedMonotoneConvergenceSealUp$ and another downstream read consumes $W$ through $\RealCauchyWitnessGridUp$. If both reads preserve the displayed source, tail, dyadic-radius, transport, continuation, provenance, and local naming rows, then they determine the same visible $\RealUp$ seal row $Q$ and the same finite route through $\CauchyModulusExtractionUp$, $\CauchySealBudgetSynchronizerUp$, $\CauchyWitnessLedgerUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\CauchyLimitSealUp$.

No such pair of reads can fork into selected limits, quotient equality, host real equality, choice rows, hidden tail oracles, ambient completeness objects, open-cover compactness rows, or alternate completion routes.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_convergence\_grid\_fork\_coherence}
\begin{proof}
Start with source-row exhaustion. Theorem~\ref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion} confines both consumers to the same packet coordinates $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so neither the convergence-seal side nor the grid side has an additional carrier coordinate on which a second terminal seal could be named.

Next lock the seal and tail rows. Theorems~\ref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} and~\ref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy} force every preserved convergence-seal read and every preserved tail-seal read through the same public source, tail, dyadic, regular-sequence, limit-seal, and $\RealUp$ rows. In particular, the visible terminal row is $Q$ once the transport, continuation, provenance, and local naming rows $H,C,P,N$ are fixed.

Now compare the two consumer routes. Theorem~\ref{thm:bounded-monotone-cauchy-witness-selector-free-real-route} excludes a second $\RealUp$-facing route outside the displayed source, tail, dyadic, limit-seal, Real-seal, and structural rows, while \autoref{thm:bounded-monotone-cauchy-witness-dyadic-radius-budget-preservation} preserves the dyadic-radius budget along the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ passage.

Finally apply root tail-budget exactness. Theorem~\ref{thm:bounded-monotone-cauchy-witness-root-tail-budget-exactness} identifies the root-source tail-seal read with the finite route through $\CauchyModulusExtractionUp$, $\CauchySealBudgetSynchronizerUp$, $\CauchyWitnessLedgerUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\CauchyLimitSealUp$. Since both consumers read the same carrier coordinates and the same row $Q$, there is no remaining coordinate from which they could fork into distinct terminal $\RealUp$ seals or any of the excluded completion mechanisms.
\end{proof}

\begin{corollary}[Bounded monotone Cauchy witness source-exhaust determinacy]
\label{cor:bounded-monotone-cauchy-witness-source-exhaust-determinacy}
Let
$$
W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)
$$
be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Once the displayed source rows $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ and structural rows $H,C,P,N$ are fixed, every accepted consumer-facing use of $W$ that asks for a convergence-seal route, a $\RealUp$-seal normal form, a criterion-ledger readback, a root-source tail-seal chain, or a grid comparison named by this chapter determines the same finite source-exhaust normal form:
$$
\MonotoneCauchyUp,\quad
\RegularCauchyTailMeetUp,\quad
\CauchyCriterionUp,\quad
\StreamNameUp,\quad
\DyadicRatCoreUp,\quad
\RegSeqRatUp,\quad
\CauchyLimitSealUp,\quad
\RealUp,
$$
with terminal visible seal row $Q$ and with the same displayed tail-budget rows when the root-source tail-seal chain is requested. No accepted use preserving the cited local rows may introduce a hidden coordinate, a duplicate classifier source, a selected limit, quotient equality, host real equality, choice row, hidden tail oracle, ambient completeness object, open-cover compactness row, or alternate completion route as a competing normal form or exactness decision.
\end{corollary}
\begin{proof}
Start with source-row exhaustion. By \autoref{thm:bounded-monotone-cauchy-witness-source-row-exhaustion}, every source-facing read of $W$ is one of $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Hence an accepted consumer use whose local rows are fixed has no second source socket from which to read a hidden coordinate or duplicate classifier source.

Apply convergence-seal route determinacy. The theorem \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-route-determinacy} fixes the public convergence-seal route through $\MonotoneCauchyUp$, $\RegularCauchyTailMeetUp$, $\CauchyCriterionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$. It also excludes routes that skip one of these rows or replace the route by selected limits, quotient equality, host real equality, trichotomy, ambient completeness, open-cover compactness, or an alternate tail selector.

The same fixed route controls the named consumer decisions. The $\RealUp$-seal normal form is exhausted by \autoref{thm:bounded-monotone-cauchy-witness-tail-real-seal-route-totality}, and \autoref{thm:bounded-monotone-cauchy-witness-tail-seal-row-determinacy} fixes the visible terminal row as $Q$ once the source, tail, seal, transport, continuation, provenance, and local naming rows are preserved. The criterion-ledger readback is exact by \autoref{thm:bounded-monotone-cauchy-witness-cauchy-ledger-readback-exactness}, and the root-source tail-seal chain is the finite budget route of \autoref{thm:bounded-monotone-cauchy-witness-root-tail-budget-exactness}. For paired convergence-seal and grid consumers, \autoref{thm:bounded-monotone-cauchy-witness-convergence-grid-fork-coherence} identifies the same visible $\RealUp$ seal row and the same finite dyadic, regular-sequence, and limit-seal passage.

Therefore every accepted consumer-facing use that preserves the cited local rows factors through the displayed source-exhaust normal form and the corresponding exactness decision already named by the chapter. Any proposed competing use would require either an additional source coordinate, ruled out by source-row exhaustion, or an alternate public route, ruled out by convergence-seal route determinacy and the named readback and seal determinacy theorems.
\end{proof}
