\begin{theorem}[Bounded monotone Cauchy witness root extraction]
\label{thm:bounded-monotone-cauchy-witness-root-extraction}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. The root extraction route read by any downstream $\BoundedMonotoneConvergenceSealUp$ consumer is the finite $\BHist$ witness packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
Here $S$ is the displayed bounded monotone source, $F$ is the regular rational row, $\sigma$ is the stream schedule, $\mu$ is the Cauchy tail witness, $\lambda$ is the dyadic tolerance and upper-bound ledger, $I$ is the located interval trap, and $Q$ is the $\RealUp$ seal row. The rows $H,C,P,N$ keep the extraction inside $\hsame$ transport, $\Cont$ continuation, $\Pkg$ provenance, and local $\NameCert_{\BoundedMonotoneCauchyWitnessUp}$ naming.

Consequently the root consumer reads a finite witness packet. It does not read a selected limit, quotient real, host real equality, trichotomy, ambient completeness claim, open-cover compactness row, or choice-like tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_extraction}
\begin{proof}
Project the carrier of \autoref{def:bounded-monotone-cauchy-witness-carrier}. Its visible coordinates are exactly $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, and the local NameCert obligations force the source, witness, trap, seal, transport, continuation, provenance, and naming reads through those coordinates.

Use the window and finite-observation locks. By \autoref{thm:bounded-monotone-cauchy-witness-window-coverage} and \autoref{thm:bounded-monotone-cauchy-witness-finite-observation-lock}, any tail request first enters the displayed source $S$, regular handoff $F$, schedule $\sigma$, witness $\mu$, and dyadic ledger $\lambda$ before it can reach $I$ or $Q$.

Finally apply the convergence-seal input package of \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-package}. That theorem identifies the downstream seal inputs with the same rows of $W$, so the root extraction has no coordinate from which an excluded completion object or choice-like selector could be produced.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness limit-seal handoff]
\label{thm:bounded-monotone-cauchy-witness-limit-seal-handoff}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. The handoff from $W$ to every $\CauchyLimitSealUp$ and $\RealUp$ consumer factors through the finite route
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The source row $S$, regular rational row $F$, stream schedule $\sigma$, tail witness $\mu$, dyadic ledger $\lambda$, located trap $I$, and Real seal row $Q$ are transported only through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ routes of the carrier.

Thus a limit-seal consumer receives the compatibility boundary carried by the witness packet. It receives no selected limiting representative, quotient-real construction, host equality proof, trichotomy split, ambient completeness principle, or compactness certificate.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_limit\_seal\_handoff}
\begin{proof}
Start with the Real seal boundary and tail-seal synchronization. Theorems \autoref{thm:bounded-monotone-cauchy-witness-real-seal-boundary} and \autoref{thm:bounded-monotone-cauchy-witness-tail-seal-synchronization} place the seal-facing suffix after the same source, regular, schedule, witness, dyadic, and located-trap rows.

Next use the trap-seal exactness and seal-route naturality. The exactness theorem fixes $I$ and $Q$ to the scheduled tail envelope, while \autoref{thm:bounded-monotone-cauchy-witness-seal-route-naturality} compares the source, criterion-tail, and Real-seal readings through the same public route.

The local transport rows close the handoff. Since $H,C,P,N$ are the only carrier rows for $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ movement, the $\CauchyLimitSealUp$ and $\RealUp$ consumers can only read the finite witness packet and cannot import any excluded completion principle.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness monotone-bound route]
\label{thm:bounded-monotone-cauchy-witness-monotone-bound-route}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. The monotone-bound route used by the bounded monotone convergence surface is the route from the displayed bounded source $S$ through the regular rational row $F$, stream schedule $\sigma$, Cauchy tail witness $\mu$, dyadic tolerance ledger $\lambda$, located interval trap $I$, and Real seal row $Q$, with $H,C,P,N$ supplying $\hsame$ transport, $\Cont$ continuation, $\Pkg$ provenance, and local $\NameCert$ naming.

Every downstream consumer that asks for bounded monotone convergence through $W$ therefore reads the same finite $\BHist$ route. The route supplies monotonicity, upper-bound, regularity, Cauchy-tail, tolerance, trap, and seal evidence, but it does not supply selected limits, quotient real equality, host real equality, trichotomy, ambient completeness, or open-cover compactness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_monotone\_bound\_route}
\begin{proof}
Begin with the source row scope and generator range exactness. These identify $S$ as the bounded monotone source coordinate and keep generator, monotonicity, and upper-bound reads inside the displayed source row.

Pass from the source to the tail service. The tail-window service and Cauchy modulus-extraction factorization route tolerance requests through $F,\sigma,\mu,\lambda$, so the bounded source is connected to a regular rational Cauchy witness by displayed rows rather than by a hidden subsequence or selected limiting object.

Finally use the located trap factorization and Real seal schedule exhaustion. They place $I$ and $Q$ after the same dyadic and scheduled-tail route, while the ledger exhaustion theorem leaves no public coordinate beyond $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. The monotone-bound route is therefore a finite BEDC witness route and not an ambient completeness claim.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root seal route exhaustion]
\label{thm:bounded-monotone-cauchy-witness-root-seal-route-exhaustion}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\BoundedMonotoneConvergenceSealUp$, $\CauchyLimitSealUp$, or $\RealUp$ consumer of $W$ factors through exactly the displayed witness rows
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
and through the sibling route chain
$$
\MonotoneCauchyUp \longmapsto \CauchyCriterionUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \CauchyLimitSealUp \longmapsto \RealUp.
$$
Thus the root seal route is exhausted by the extraction, limit-seal handoff, monotone-bound route, and convergence-seal input package. It contains no selected limit, quotient real equality, host equality, trichotomy, compactness, ambient completeness, or choice-like tail selector.

The sibling route is the concrete L10 chain of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-cauchylimitseal-namecert}, and \autoref{ch:concrete-instances-real-namecert}; the witness packet consumes their finite-window, dyadic-ledger, regular-source, limit-seal, and Real-seal rows before any convergence-seal consumer reads it.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_seal\_route\_exhaustion}
\begin{proof}
First apply \autoref{thm:bounded-monotone-cauchy-witness-root-extraction}. It projects the accepted carrier to the finite witness packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ and rules out any root coordinate outside that packet.

Next apply \autoref{thm:bounded-monotone-cauchy-witness-limit-seal-handoff} and \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route}. The handoff theorem places every $\CauchyLimitSealUp$ and $\RealUp$ read on the same finite packet, while the monotone-bound theorem routes the bounded monotone convergence surface through $S,F,\sigma,\mu,\lambda,I,Q$ with $H,C,P,N$ supplying transport, continuation, provenance, and naming.

Finally apply \autoref{thm:bounded-monotone-cauchy-witness-convergence-seal-input-package}. That package identifies the completion-facing suffix with the sibling chain from $\MonotoneCauchyUp$ through $\RealUp$. Since all three root-facing consumer types enter through the preceding finite rows and the package supplies the only seal-facing continuation, no selected limit, quotient equality, host equality, trichotomy, compactness, ambient completeness, or choice-like tail selector remains available.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root tail-window totality]
\label{thm:bounded-monotone-cauchy-witness-root-tail-window-totality}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing consumer of $W$ that asks for a convergence-seal, limit-seal, or real-seal input must first consume the displayed $\StreamNameUp$ tail window carried by $\sigma$ together with the Cauchy witness row $\mu$ and the dyadic ledger $\lambda$.

Thus the root route through $W$ has a total tail-window obligation row. It passes through the displayed source $S$, regular rational row $F$, scheduled window $\sigma$, witness $\mu$, and ledger $\lambda$ before any located trap or $\RealUp$ seal threshold can be read, and it contains no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_tail\_window\_totality}
\begin{proof}
Start with the carrier definition. The accepted packet exposes $\sigma$ as the $\StreamNameUp$ window schedule, $\mu$ as the Cauchy tail witness, and $\lambda$ as the dyadic tolerance and upper-bound ledger; no separate tail service is a carrier coordinate.

Apply root extraction and the monotone-bound route. \autoref{thm:bounded-monotone-cauchy-witness-root-extraction} projects every root read to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, while \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route} places the bounded monotone source before the same scheduled tail service.

Finally use the limit-seal handoff and root seal route exhaustion. The handoff theorem keeps seal-facing consumers on the displayed packet, and \autoref{thm:bounded-monotone-cauchy-witness-root-seal-route-exhaustion} leaves no route around the sibling chain through $\StreamNameUp$. Therefore tail-window consumption is total for the root route and the excluded completion objects are not available.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root located-trap stability]
\label{thm:bounded-monotone-cauchy-witness-root-located-trap-stability}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing consumer that has passed through the displayed tail window must preserve the $\LocatedIntervalUp$ trap row $I$ as the next pre-seal enclosure. Transport through $H$ and replay through $C$ may move the displayed rows componentwise, but the root route cannot replace $I$ by an ambient interval choice, host equality, quotient real equality, trichotomy, completeness, compactness, or a selected limiting representative.

Consequently the located-trap obligation is stable under the accepted root route for $\BoundedMonotoneConvergenceSealUp$, $\CauchyLimitSealUp$, and $\RealUp$ consumers.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_located\_trap\_stability}
\begin{proof}
Read the located row from the carrier. The definition makes $I$ the unique $\LocatedIntervalUp$ trap row and places it after $S,F,\sigma,\mu,\lambda$ and before the seal row $Q$.

Use the root extraction theorem to confine the consumer surface. Any root consumer starts from the displayed packet $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so the only available movement of the trap row is the componentwise transport and continuation data already carried by $H$ and $C$.

Next apply the limit-seal handoff and monotone-bound route. They both route seal-facing and convergence-facing reads through the same scheduled tail and located-trap suffix, so preserving the root route also preserves $I$ as the pre-seal enclosure.

The root seal route exhaustion theorem then rules out replacement rows. Since no selected limit, quotient equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like trap selector is present in the exhausted packet, the located trap remains stable for all three root-facing consumer types.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root Real-seal threshold exhaustion]
\label{thm:bounded-monotone-cauchy-witness-root-real-seal-threshold-exhaustion}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\RealUp$ threshold consumed from $W$ is reached only after the displayed tail window $\sigma,\mu,\lambda$ and the located trap $I$ have been consumed. The seal row $Q$ is therefore a threshold route over the finite witness packet, not a selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selector.

Equivalently, a root consumer cannot expose a $\RealUp$ seal threshold from $W$ unless it has already traversed the accepted packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Begin with the carrier and the Real seal boundary. The carrier lists $Q$ only after the regular rational row, scheduled window, Cauchy witness, dyadic ledger, and located trap, and the existing seal boundary keeps every $\RealUp$ read tied to that order.

Apply root extraction, then attach the limit-seal handoff. Root extraction supplies the finite packet, and the handoff theorem says that $\CauchyLimitSealUp$ and $\RealUp$ consumers read the same packet through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ routes.

Now use the monotone-bound route and root tail-window totality. The monotone-bound route places the source and bound data before $F,\sigma,\mu,\lambda$, while \autoref{thm:bounded-monotone-cauchy-witness-root-tail-window-totality} makes the tail-window obligation unavoidable before any pre-seal or seal row is reached.

Finally apply located-trap stability and root seal route exhaustion. The trap theorem fixes $I$ as the pre-seal enclosure, and the exhaustion theorem leaves the seal-facing suffix with no coordinate outside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Hence the $\RealUp$ threshold consumption is exhausted by the displayed root route and exports none of the excluded completion principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessRootRealSealThresholdExhaustion}

\begin{theorem}[Bounded monotone Cauchy witness grid route compatibility]
\label{thm:bounded-monotone-cauchy-witness-grid-route-compatibility}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and suppose its root route consumes an accepted $\RealCauchyWitnessGridUp$ packet $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$. Then the root route must read the selector budget $B$, witness ledger $L$, completion-seal classifier $K$, and tail-witness envelope $T$ of $G$ before it reaches the $\RealUp$ seal row $Q$ of $W$.

Thus the bounded monotone witness does not run a completion route parallel to the grid. Its Real-facing threshold is compatible with the grid carrier of \autoref{def:real-cauchy-witness-grid-carrier}: selector exactness, witness-ledger accounting, classifier exposure, and tail-envelope readback are consumed before the final $\RealUp$ row is available.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_grid\_route\_compatibility}
\begin{proof}
Project the accepted witness packet by \autoref{thm:bounded-monotone-cauchy-witness-root-extraction}. This confines the root route to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ and leaves no completion-facing coordinate outside the displayed packet.

Attach the limit-seal handoff and monotone-bound route. Theorems \autoref{thm:bounded-monotone-cauchy-witness-limit-seal-handoff} and \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route} place every $\CauchyLimitSealUp$ and $\RealUp$ read after the source, regular, schedule, witness, dyadic, and located-trap rows.

Now read the grid packet. By \autoref{thm:real-cauchy-witness-grid-selector-exactness} and \autoref{thm:real-cauchy-witness-grid-real-handoff}, the grid route reaches $\RealUp$ only after $B,S_G,R_G,L,T,K,E_G,H_G,C_G,P_G,N_G$ have been consumed.

Finally use \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-threshold-exhaustion}. Since the threshold row $Q$ is reached only at the seal end of the bounded-monotone route, a route that consumes $G$ must first pass through the grid selector budget, witness ledger, completion classifier, and tail envelope.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness grid ledger non-escape]
\label{thm:bounded-monotone-cauchy-witness-grid-ledger-nonescape}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier whose root route consumes an accepted $\RealCauchyWitnessGridUp$ packet $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$. The grid handoff exports only the displayed selector-budget, witness-ledger, completion-seal classifier, tail-witness, StreamName, RegSeqRat, RealUp, transport, continuation, provenance, and local naming rows of $G$ together with the displayed rows of $W$.

It exposes no selected limit, quotient real equality, host equality, trichotomy, countable choice, ambient completeness, open-cover compactness, hidden selector enlargement, or choice-like tail selector.
\end{theorem}
\begin{proof}
Start from the grid non-escape theorem, \autoref{thm:real-cauchy-witness-grid-nonescape}. It says that an accepted grid exports only $B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G$ and none of the excluded completion or host-level objects.

Use grid route compatibility to attach that non-escape result to the bounded monotone witness. The compatibility theorem forces the grid selector, ledger, classifier, and tail rows to be read before the witness route reaches its $\RealUp$ seal row.

Now apply root seal route exhaustion and Real-seal threshold exhaustion for $W$. These theorems leave the bounded-monotone route inside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ and exclude selected limits, quotient equality, host equality, trichotomy, compactness, ambient completeness, and choice-like selectors from the witness side.

The two packets therefore compose without adding an escape coordinate. The grid contributes only its displayed ledger rows, and the bounded monotone witness contributes only its displayed root rows.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_grid\_ledger\_nonescape}

\begin{theorem}[Bounded monotone Cauchy witness diagonal-limit compatibility pullback]
\label{thm:bounded-monotone-cauchy-witness-diagonal-limit-compatibility-pullback}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Suppose its root route consumes an accepted $\RealCauchyWitnessGridUp$ packet $G=(B,L_G,K_G,T_G,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$ and an accepted $\DiagonalLimitCompatibilityUp$ packet
$$
D=(R_D,T_D,S_D,D_D,W_D,Q_D,L_D,H_D,C_D,P_D,N_D)
$$
through the budget-seal factorization route of \autoref{thm:diagonal-limit-compatibility-root-budget-seal-factorization}. Then every terminal $\RealUp$ or completion-seal read from the root route factors through one finite pullback surface consisting of the bounded source $S$, scheduled $\StreamNameUp$ window $\sigma$, dyadic ledger $\lambda$, $\RegSeqRatUp$ handoff $F$, located trap $I$, grid selector and witness ledger rows $B,L_G,K_G,T_G,S_G,R_G,E_G$, diagonal budget rows $R_D,T_D,S_D,D_D,W_D,Q_D,L_D$, the $\CauchyLimitSealUp$ boundary, the terminal $\RealUp$ seal rows $Q,E_G,L_D$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows
$$
H,H_G,H_D,\quad C,C_G,C_D,\quad P,P_G,P_D,\quad N,N_G,N_D.
$$

The pullback exports no selected limit, quotient real equality, host equality, trichotomy, countable choice, ambient completeness, open-cover compactness, hidden selector enlargement, or unlisted tail selector.
\end{theorem}
\begin{proof}
First project the bounded monotone root packet. By \autoref{thm:bounded-monotone-cauchy-witness-root-extraction}, every root-facing read of $W$ is confined to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, with no external completion coordinate.

Next attach the grid route. The compatibility theorem \autoref{thm:bounded-monotone-cauchy-witness-grid-route-compatibility} places the selector budget, witness ledger, classifier, and tail rows of $G$ before the $\RealUp$ seal row of $W$, and \autoref{thm:bounded-monotone-cauchy-witness-grid-ledger-nonescape} says that the grid contributes only the displayed rows $B,L_G,K_G,T_G,S_G,R_G,E_G,H_G,C_G,P_G,N_G$.

Now read the diagonal-limit compatibility packet. The budget-seal factorization of \autoref{thm:diagonal-limit-compatibility-root-budget-seal-factorization} sends terminal Real and completion-seal consumers through $R_D,T_D,S_D,D_D,W_D,Q_D,L_D,H_D,C_D,P_D,N_D$, while \autoref{thm:diagonal-limit-compatibility-root-provenance-exhaustion} keeps the same route inside its displayed provenance and local naming rows.

Finally apply terminal pullback non-escape for the diagonal route, \autoref{thm:diagonal-limit-compatibility-terminal-pullback-consumer-nonescape}. The bounded source, grid ledger, diagonal budget route, CauchyLimitSeal boundary, RealUp seal, and all transport, continuation, package, and naming rows have already been listed. Since the exhausted finite packet has no coordinate for selected limits, quotient equality, host equality, trichotomy, choice, completeness, compactness, hidden selector growth, or tail-selector enlargement, every terminal read factors through exactly the displayed pullback surface.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness grid root package]
\label{thm:bounded-monotone-cauchy-witness-grid-root-package}
An accepted $\BoundedMonotoneCauchyWitnessUp$ carrier whose root route consumes an accepted $\RealCauchyWitnessGridUp$ packet forms a finite L10 root package through \autoref{ch:concrete-instances-real-cauchy-witness-grid-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-cauchylimitseal-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

The package reads the grid selector budget, witness ledger, completion-seal classifier, and tail-witness envelope before the bounded-monotone root route reaches the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ sibling rows. It remains a finite root package and not an import of completeness.
\end{theorem}
\begin{proof}
First project the bounded monotone root packet by root extraction. The visible route is $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, so the package has a finite witness side.

Next apply the limit-seal handoff, monotone-bound route, and root seal route exhaustion. These results identify the sibling chain through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ as the only seal-facing continuation of the bounded-monotone packet.

Attach the Real Cauchy witness grid by \autoref{thm:bounded-monotone-cauchy-witness-grid-route-compatibility}. The grid rows are consumed before the Real seal row, with selector, ledger, classifier, and tail-envelope reads supplied by the carrier of \autoref{ch:concrete-instances-real-cauchy-witness-grid-namecert}.

Finally apply \autoref{thm:bounded-monotone-cauchy-witness-grid-ledger-nonescape}. The composed L10 package has no coordinate for selected limits, quotient real equality, host equality, trichotomy, countable choice, ambient completeness, compactness, hidden selector state, or choice-like tail selection.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root source-seal totality]
\label{thm:bounded-monotone-cauchy-witness-root-source-seal-totality}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing consumer from the bounded monotone source to a $\RealUp$ seal factors through the displayed packet
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The route consumes the $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ sibling rows, and it exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, or choice-like selector.
\end{theorem}
\begin{proof}
Start with root extraction. \autoref{thm:bounded-monotone-cauchy-witness-root-extraction} confines every root read of $W$ to the displayed carrier rows, so no root-facing consumer can begin from an external completion object.

Next attach the bounded monotone source and the seal handoff. The monotone-bound route places the source data before the scheduled tail, while the limit-seal handoff sends $\CauchyLimitSealUp$ and $\RealUp$ consumers through the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The tail-window and trap theorems close the middle of the route. Root tail-window totality forces consumption of $\sigma,\mu,\lambda$ before any seal-facing row is reached, and located-trap stability keeps $I$ as the pre-seal enclosure rather than replacing it by an ambient interval choice.

Finally apply Real-seal threshold exhaustion. The threshold theorem consumes the seal row $Q$ only after the displayed source, tail, and trap rows, and root seal route exhaustion leaves no coordinate outside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$. Therefore the full source-to-seal route is total on the finite packet and exports none of the excluded completion principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_source\_seal\_totality}

\begin{theorem}[Bounded monotone Cauchy witness root synchronizer handoff]
\label{thm:bounded-monotone-cauchy-witness-root-synchronizer-handoff}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\BoundedMonotoneConvergenceSealUp$, $\CauchyLimitSealUp$, $\CauchySealBudgetSynchronizerUp$, $\RealObservationBudgetUp$, or $\RealUp$ consumer of $W$ factors through the same finite route
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N.
$$
The synchronizer handoff uses the sibling L10 chain
$$
\StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \CauchyLimitSealUp \longmapsto \RealUp
$$
after the displayed bounded monotone source, schedule, tail witness, dyadic ledger, located trap, seal row, transport, continuation, provenance, and local naming rows have been consumed.

Consequently the root packet supplies the shared synchronizer-facing surface for the limit-seal and Real-observation-budget routes. It supplies no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, hidden synchronizer state, or choice-like selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessCarrier\_root\_synchronizer\_handoff}
\begin{proof}
Begin with root extraction and source-seal totality. \autoref{thm:bounded-monotone-cauchy-witness-root-extraction} confines every root read of $W$ to the displayed packet, while \autoref{thm:bounded-monotone-cauchy-witness-root-source-seal-totality} carries that packet from the bounded monotone source through the $\RealUp$ seal.

Next attach the limit-seal and synchronizer-facing legs. The limit-seal handoff theorem places $\CauchyLimitSealUp$ and $\RealUp$ consumers on the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and root seal route exhaustion identifies the sibling L10 chain ending at $\RealUp$ as the only seal-facing continuation.

The middle rows are forced by the tail and trap obligations. Root tail-window totality consumes $\sigma,\mu,\lambda$ before any seal-facing read, and located-trap stability keeps $I$ as the pre-seal enclosure rather than replacing it by an ambient interval choice.

Finally use Real-seal threshold exhaustion. The $\RealUp$ threshold is reached only after $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ have been traversed, so a $\CauchySealBudgetSynchronizerUp$ or $\RealObservationBudgetUp$ consumer has no hidden synchronizer coordinate beyond the displayed route. The excluded completion and choice principles are absent from the packet and cannot be exported by the handoff.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness synchronizer-grid route]
\label{thm:bounded-monotone-cauchy-witness-synchronizer-grid-route}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$ be an accepted $\RealCauchyWitnessGridUp$ packet consumed on the root route of $W$. Every root-facing synchronizer consumer of $W$ that also consumes $G$ must route through the same finite witness rows
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
and through the grid rows $B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G$ before reaching any $\RealUp$ seal.

The route exports no selected limit, quotient real equality, host equality, trichotomy, countable choice, ambient completeness, open-cover compactness, hidden synchronizer state, or detached grid selector.
\end{theorem}
\begin{proof}
Begin with the root synchronizer handoff. It sends every $\CauchySealBudgetSynchronizerUp$, $\RealObservationBudgetUp$, and $\RealUp$ consumer through the displayed rows of $W$ and leaves no hidden synchronizer coordinate outside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Attach the grid by grid route compatibility. Any accepted route that consumes $G$ reaches the grid selector budget, witness ledger, completion classifier, and tail envelope before the $\RealUp$ seal row $Q$ of $W$ is read.

Use grid ledger non-escape to identify the grid contribution. The grid packet contributes only $B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G$ together with the displayed rows of $W$, and it does not supply a detached selector or ambient completion principle.

Finally apply root Real-seal threshold exhaustion. The $\RealUp$ seal can be consumed only after the finite bounded-source, tail-window, located-trap, synchronizer, and grid rows have already been traversed, so none of the excluded selected-limit, equality, choice, completeness, compactness, hidden-state, or detached-selector data is exported.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root tail-seal nesting]
\label{thm:bounded-monotone-cauchy-witness-root-tail-seal-nesting}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Every root-facing $\BoundedMonotoneConvergenceSealUp$, $\CauchyLimitSealUp$, $\CauchySealBudgetSynchronizerUp$, $\RealObservationBudgetUp$, or $\RealUp$ consumer of $W$ is forced through the nested finite order
$$
S,F \longrightarrow \sigma,\mu,\lambda \longrightarrow I \longrightarrow Q \longrightarrow H,C,P,N.
$$
The $S,F$ stage supplies the bounded monotone source and dyadic bound data; the $\sigma,\mu,\lambda$ stage supplies the scheduled tail-window data; the $I$ stage supplies the located trap; the $Q$ stage supplies the Real-seal threshold; and $H,C,P,N$ carry transport, route replay, provenance, and local naming.

Consequently the L10 source-to-seal route through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, $\RealObservationBudgetUp$, and $\RealUp$ remains inside the displayed packet. It exports no selected limit, quotient real equality, host equality, trichotomy, ambient completeness, open-cover compactness, hidden synchronizer state, or choice-like selector.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedMonotoneCauchyWitnessUp.BoundedMonotoneCauchyWitnessTailSealNesting}
\begin{proof}
First confine the packet. Root extraction, \autoref{thm:bounded-monotone-cauchy-witness-root-extraction}, says that every root-facing read of $W$ is a read of the displayed carrier rows $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$.

Next force the tail-window stage. By \autoref{thm:bounded-monotone-cauchy-witness-root-tail-window-totality}, any root-facing pre-seal or seal consumer must pass through $\sigma,\mu,\lambda$ after the source and bound rows $S,F$.

Now place the trap and threshold rows. Located-trap stability, \autoref{thm:bounded-monotone-cauchy-witness-root-located-trap-stability}, keeps $I$ as the pre-seal enclosure, and Real-seal threshold exhaustion, \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-threshold-exhaustion}, places $Q$ before the $\RealUp$ threshold is consumed.

Finally apply the synchronizer handoff, \autoref{thm:bounded-monotone-cauchy-witness-root-synchronizer-handoff}. It sends $\CauchySealBudgetSynchronizerUp$ and $\RealObservationBudgetUp$ consumers through the same finite surface as the $\CauchyLimitSealUp$ and $\RealUp$ consumers, with $H,C,P,N$ carrying transport, route replay, provenance, and naming rather than an external synchronizer coordinate.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness grid budget precedes seal]
\label{thm:bounded-monotone-cauchy-witness-grid-budget-precedes-seal}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let its root route consume an accepted $\RealCauchyWitnessGridUp$ packet $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$. Along that finite route the selector budget $B$, witness ledger $L$, completion-seal classifier $K$, and tail envelope $T$ of $G$ must be read before the route exposes the $\RealUp$ seal row $Q$ of $W$.

Thus the grid budget is a pre-seal obligation on the same root route. The composed packet exports no selected limit, quotient real equality, host equality, trichotomy, countable choice, ambient completeness, hidden grid selector, or choice-like tail selector.
\end{theorem}
\begin{proof}
First attach the grid route to the bounded-monotone root packet. By \autoref{thm:bounded-monotone-cauchy-witness-grid-route-compatibility}, any route consuming $G$ reaches the grid selector budget, witness ledger, completion classifier, and tail envelope before it reaches the $\RealUp$ seal row $Q$ of $W$.

Next use the ledger non-escape theorem. \autoref{thm:bounded-monotone-cauchy-witness-grid-ledger-nonescape} says that the grid handoff contributes only $B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G$ together with the displayed rows of $W$, and does not add selected limits, quotient equality, host equality, trichotomy, countable choice, ambient completeness, or hidden selector state.

Now place this order at the Real threshold. \autoref{thm:bounded-monotone-cauchy-witness-root-real-seal-threshold-exhaustion} forces any $\RealUp$ threshold read from $W$ to occur only after the finite source, tail-window, and located-trap rows have already been consumed.

Finally apply tail-seal nesting, \autoref{thm:bounded-monotone-cauchy-witness-root-tail-seal-nesting}. It nests the route as a single finite chain ending in $Q$ and then $H,C,P,N$, so the grid budget rows cannot be exposed on a separate completion route after the seal. The same route therefore reads $B,L,K,T$ before exposing $Q$, and none of the excluded completion principles is exported.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness route tightening]
\label{thm:bounded-monotone-cauchy-witness-route-tightening}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and let its root route consume an accepted $\RealCauchyWitnessGridUp$ packet $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$. The accepted witness route factors through the monotone-bound rows, the tail-window rows, the grid-budget rows, and the $\RealUp$ seal row in the finite order
$$
S,F \longrightarrow \sigma,\mu,\lambda \longrightarrow B,L,K,T \longrightarrow I \longrightarrow Q \longrightarrow H,C,P,N.
$$
The route is therefore a tightening of the displayed $\BHist$ packet: every Real-seal read is preceded by bounded-source data, scheduled Cauchy-modulus data, selector-budget and witness-ledger data, and the located trap. It does not import a selected limit, host real equality, quotient real equality, completeness, compactness, trichotomy, or choice data.
\end{theorem}
\begin{proof}
First apply root extraction and the monotone-bound route. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-extraction} and~\ref{thm:bounded-monotone-cauchy-witness-monotone-bound-route} confine the accepted carrier to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$ and place the bounded-source rows before the scheduled tail service.

Next use root tail-window totality. It makes $\sigma,\mu,\lambda$ unavoidable before any located-trap or Real-seal row can be consumed, so the Cauchy-modulus route is already finite inside the displayed packet.

Now attach the grid side by grid budget precedence. The theorem \autoref{thm:bounded-monotone-cauchy-witness-grid-budget-precedes-seal} places $B,L,K,T$ before $Q$ on the same root route, not on a parallel completion route.

Finally use the limit-seal handoff and synchronizer handoff. These hand the resulting finite route to $\CauchyLimitSealUp$, $\CauchySealBudgetSynchronizerUp$, $\RealObservationBudgetUp$, and $\RealUp$ consumers through $H,C,P,N$, leaving no carrier coordinate for the excluded completion or choice principles.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness schedule factorization]
\label{thm:bounded-monotone-cauchy-witness-schedule-factorization}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Before any downstream $\RealUp$ seal read from $W$, the schedule row $\sigma$, the Cauchy-modulus witness row $\mu$, and the dyadic tolerance ledger $\lambda$ appear as finite $\BHist$ rows of the same accepted packet, transported only by $H$, replayed only by $C$, packaged only by $P$, and named only by $N$.

Consequently the Real-seal consumer receives finite schedule and modulus data rather than a selected tail, host sequence equality, ambient Cauchy-completeness principle, or choice-like modulus selector.
\end{theorem}
\begin{proof}
Start from root extraction. It identifies $\sigma,\mu,\lambda$ as visible carrier rows and leaves no separate schedule service outside $W$.

Use root tail-window totality to force the order. Every convergence-seal, limit-seal, synchronizer, observation-budget, or Real-seal consumer must consume $\sigma,\mu,\lambda$ before the located-trap and seal rows.

Apply route tightening to the resulting packet. The tightened route keeps the schedule, modulus, dyadic ledger, grid-budget rows, located trap, and seal row on one finite $\BHist$ route.

The limit-seal handoff and synchronizer handoff then move that finite route through $H,C,P,N$. Since those are the only transport, continuation, package, and naming rows, no selected tail, host sequence equality, completeness principle, or choice-like modulus selector is available to the Real-seal consumer.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness Real-seal consumer exhaustion]
\label{thm:bounded-monotone-cauchy-witness-real-seal-consumer-exhaustion}
Every downstream $\RealUp$-seal consumer of an accepted $\BoundedMonotoneCauchyWitnessUp$ packet $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$, together with any accepted $\RealCauchyWitnessGridUp$ packet consumed on its root route, is exhausted by the displayed rows
$$
S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N
$$
and by the grid-budget rows $B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G$ when such a grid packet is present. No downstream Real-seal consumer can import selected limits, host real equality, quotient real equality, real completeness, compactness, trichotomy, countable choice, hidden grid selector state, or choice-like tail data.
\end{theorem}
\begin{proof}
First confine the witness route by root extraction and limit-seal handoff. These theorems identify the finite rows of $W$ and make every $\CauchyLimitSealUp$ or $\RealUp$ read pass through them.

Next apply schedule factorization. It records that $\sigma,\mu,\lambda$ are finite $\BHist$ rows before the Real-seal read, with $H,C,P,N$ carrying only displayed transport, route replay, provenance, and naming.

If the root route consumes a grid packet, use grid budget precedence. The rows $B,L,K,T$ are read before $Q$, and the remaining grid rows are exactly the carrier, handoff, transport, continuation, provenance, and naming rows already listed by the grid package.

Finally apply the synchronizer handoff and route tightening. They exhaust the Real-seal, synchronizer, and observation-budget consumers by the displayed witness and grid rows, so none of the excluded selected-limit, host-equality, completeness, compactness, trichotomy, choice, or hidden-selector data can be imported.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness four-face budget correspondence]
\label{thm:bounded-monotone-cauchy-witness-four-face-budget-correspondence}
Every accepted bounded monotone Cauchy witness consumed by the Real-seal route factors through exactly the four licensed L10 faces
$$
\DyadicRatCoreUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp.
$$
For an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$, the $\StreamNameUp$ face is the finite observation schedule $\sigma$, the $\DyadicRatCoreUp$ face is the dyadic tolerance and upper-bound ledger $\lambda$ together with the grid selector budget when a $\RealCauchyWitnessGridUp$ packet is consumed, the $\RegSeqRatUp$ face is the regular rational readback row $F$ together with the grid readback rows, and the $\RealUp$ face is the seal row $Q$.

The correspondence is exhausted by displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It has no coordinate for quotient streams, selected host limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First confine the consumer to the witness packet. By \autoref{thm:bounded-monotone-cauchy-witness-root-extraction} and \autoref{thm:bounded-monotone-cauchy-witness-monotone-bound-route}, every root-facing read stays inside $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, with the bounded source and regular rational readback before the scheduled tail service.

Next identify the licensed faces. Theorems~\ref{thm:bounded-monotone-cauchy-witness-root-tail-window-totality} and~\ref{thm:bounded-monotone-cauchy-witness-schedule-factorization} make $\sigma,\mu,\lambda$ unavoidable before a seal read and read those rows as finite $\BHist$ data transported only by $H$, replayed only by $C$, packaged only by $P$, and named only by $N$.

Now attach the budget side. The grid-budget theorem \autoref{thm:bounded-monotone-cauchy-witness-grid-budget-precedes-seal} places the selector budget, witness ledger, completion-seal classifier, and tail envelope before $Q$ whenever a grid packet is present, and \autoref{thm:bounded-monotone-cauchy-witness-route-tightening} keeps those rows on the same Real-facing chain rather than on a parallel completion route.

Finally apply \autoref{thm:bounded-monotone-cauchy-witness-root-synchronizer-handoff} and \autoref{thm:bounded-monotone-cauchy-witness-real-seal-consumer-exhaustion}. These keep observation-budget and seal-budget consumers on the same finite surface and list all rows available to the downstream consumer. Therefore the four faces above are the entire budget correspondence, and the excluded quotient-stream, selected-limit, choice, and ambient-completeness data have no displayed carrier row from which to be read.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness uniform criterion handoff]
\label{thm:bounded-monotone-cauchy-witness-uniform-criterion-handoff}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier, and suppose a downstream $\UniformCauchyCriterionUp$ consumer reads the root route of $W$ through an accepted packet
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U).
$$
Then the bounded-source route of $W$ factors through the finite chain
$$
S,F \longrightarrow \sigma,\mu,\lambda \longrightarrow I,Q \longrightarrow I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U.
$$
The first stage supplies the displayed bounded monotone source and regular rational readback; the second supplies the $\StreamNameUp$ finite-window schedule, Cauchy tail witness, and dyadic tolerance ledger; the third supplies the located trap and $\RealUp$ seal row; and the final stage is exactly the UniformCauchyCriterion family-test surface over its finite index, shared window, shared modulus, dyadic tolerance, tail ledger, seal handoff, transport, continuation, package, and local naming rows.

The StreamName finite-window handoff and the $\RegSeqRatUp$--$\RealUp$ seal rows remain explicit throughout the chain. Thus the handoff exports no quotient streams, selected host limits, host real equality, countable choice, ambient completeness, open-cover compactness, hidden family limit, or direct $\RealUp$ bypass.
\end{theorem}
\begin{proof}
First project the bounded monotone witness. Root extraction confines every root read of $W$ to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, and root tail-window totality forces the consumer to pass through $\sigma,\mu,\lambda$ before any located-trap or seal row is available.

Next factor the schedule route. The schedule factorization theorem records $\sigma,\mu,\lambda$ as finite $\BHist$ rows transported only by $H$, replayed only by $C$, packaged only by $P$, and named only by $N$. The four-face budget correspondence then identifies the licensed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ faces that the downstream consumer may read.

Now attach the UniformCauchyCriterion packet. By \autoref{thm:uniform-cauchy-criterion-window-stability}, the family request preserves the same finite index ledger, shared window family, and shared modulus before a tail comparison is inspected. By \autoref{thm:uniform-cauchy-criterion-root-downstream-unblock}, the full criterion-facing surface is exhausted by $I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U$.

Finally bind the StreamName and regular-real handoff rows. The StreamName finite-window handoff of \autoref{thm:streamname-real-regseq-finite-window-handoff} keeps the finite observation window and $\RegSeqRatUp$ seed rows visible, while the bounded monotone root seal route and Real-seal consumer exhaustion keep the $I,Q$ suffix tied to the same regular-source and seal route. Since neither side contributes quotient streams, selected limits, host real equality, countable choice, ambient completeness, open-cover compactness, or a direct $\RealUp$ bypass, their composite handoff is exactly the finite chain displayed above.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness observation-budget grid pullback]
\label{thm:bounded-monotone-cauchy-witness-observation-budget-grid-pullback}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ carrier. Let
$$
G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)
$$
be an accepted $\RealCauchyWitnessGridUp$ packet, let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted $\UniformCauchyCriterionUp$ packet, and let
$$
O=(E_O,W_O,D_O,R_O,S_O,H_O,C_O,P_O,N_O)
$$
be an accepted $\RealObservationBudgetUp$ packet reading the same finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ ledgers, $\RegSeqRatUp$ regular readbacks, and $\RealUp$ seal rows used by the root route of $W$, the grid packet $G$, and the uniform criterion packet $U$. Then the bounded-source route, grid-budget route, uniform-criterion route, and observation-budget route determine one pullback surface before any $\RealUp$ seal is public:
$$
S,F,\sigma,\mu,\lambda,I,Q,B,L,K,T,S_G,R_G,E_G,I_U,W_U,M_U,Q_U,T_U,E_U,E_O,W_O,D_O,R_O,S_O,H,H_G,H_U,H_O,C,C_G,C_U,C_O,P,P_G,P_U,P_O,N,N_G,N_U,N_O.
$$
Every consumer of this surface first reads the root source and tail-window rows of $W$, then the grid budget rows of $G$, then the uniform-criterion rows of $U$, and finally the finite observation-budget rows that name the same windows, dyadic ledgers, regular readbacks, and seal boundary. The surface exports no quotient stream, selected host limit, host real equality, countable-choice selector, ambient completeness theorem, open-cover compactness principle, hidden family limit, or direct $\RealUp$ bypass.
\end{theorem}
\begin{proof}
First project the bounded-source route. Root extraction confines all reads of $W$ to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, and schedule factorization records $\sigma,\mu,\lambda$ as finite $\BHist$ rows transported only by $H$, replayed only by $C$, packaged only by $P$, and named only by $N$.

Next attach the grid side. The grid-budget precedence theorem places $B,L,K,T$ before the seal row $Q$ on the same root route, while the grid readback rows $S_G,R_G,E_G$ sit on the same $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces. Thus the grid packet contributes budget rows to the same surface rather than a second completion route.

Now attach the uniform criterion. The uniform-criterion handoff sends the family-test packet $U$ through the already displayed finite windows, dyadic tolerance ledger, regular readback, and seal handoff. Its rows $I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U$ therefore meet the bounded-source and grid rows along the shared L10 faces.

Finally read the observation-budget route. By \autoref{def:real-observation-budget-carrier}, \autoref{thm:real-observation-budget-window-coverage}, \autoref{thm:real-observation-budget-regseq-handoff}, \autoref{thm:real-observation-budget-real-seal-boundary}, and \autoref{thm:real-observation-budget-nonescape}, the observation-budget consumer exposes only its finite request, window, dyadic, regular-handoff, seal, transport, continuation, provenance, and naming rows. Since those rows are assumed to be the same finite windows, ledgers, readbacks, and seal rows already displayed by $W$, $G$, and $U$, the four routes share exactly the pullback surface above before any $\RealUp$ seal can be public.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness criterion-grid-synchronizer correspondence]
\label{thm:bounded-monotone-cauchy-witness-criterion-grid-synchronizer-correspondence}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Its public route to $\CauchyCriterionUp$, $\RealCauchyWitnessGridUp$, $\CauchySealBudgetSynchronizerUp$, and $\RealObservationBudgetUp$ is a single displayed correspondence before $Q$ is read as the $\RealUp$ seal: the criterion tail exposes the scheduled window and modulus ledger, the grid packet exposes the finite observation and witness-budget rows, and the synchronizer exposes the seal budget.

The correspondence is exhausted by the rows of $W$, the grid-budget rows, the criterion-tail rows, the synchronizer seal-budget rows, the observation-budget rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ names. It exports no quotient streams, selected limits, host real equality, trichotomy, ambient completeness, open-cover compactness, or choice-like tail selection.
\end{theorem}
\begin{proof}
Apply root extraction to the accepted packet $W$. This confines the public route to the bounded source, regular readback, schedule, modulus, dyadic ledger, located trap, seal, transport, route, provenance, and naming rows.

Apply root tail-window totality. The scheduled window $\sigma$, modulus witness $\mu$, and dyadic ledger $\lambda$ are read before any located-trap, synchronizer, observation-budget, or $\RealUp$ seal consumer can inspect $Q$.

Apply grid budget precedence. The $\RealCauchyWitnessGridUp$ packet contributes its finite observation and witness-budget rows before the seal row, so the grid route is a budgeted face of the same root route rather than a hidden completion route.

Apply the synchronizer handoff and the observation-budget grid pullback. The synchronizer exposes the seal budget on the same displayed chain, and the observation-budget route reads the same finite windows, dyadic ledgers, regular readbacks, and seal boundary.

Finally apply Real-seal consumer exhaustion. The downstream consumer has only the displayed witness, criterion, grid, synchronizer, observation-budget, transport, continuation, provenance, and naming rows, so the excluded quotient-stream, selected-limit, host-equality, trichotomy, completeness, compactness, and choice-like tail-selection routes have no carrier coordinate.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness root Real-seal determinacy]
\label{thm:bounded-monotone-cauchy-witness-root-real-seal-determinacy}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Let $G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)$ be an accepted $\RealCauchyWitnessGridUp$ packet, let $U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)$ be an accepted $\UniformCauchyCriterionUp$ packet, and let $O=(E_O,W_O,D_O,R_O,S_O,H_O,C_O,P_O,N_O)$ be an accepted $\RealObservationBudgetUp$ packet reading the same displayed finite-window, dyadic-ledger, regular-readback, and seal rows as the root route of $W$ and the grid and criterion packets.

Then any public $\RealUp$ seal read on the shared surface is determined by the common displayed rows of the bounded-source route, grid-budget route, uniform-criterion route, synchronizer route, and observation-budget route. If two public seal reads preserve
$$
S,F,\sigma,\mu,\lambda,I,Q,B,L,K,T,S_G,R_G,E_G,I_U,W_U,M_U,Q_U,T_U,E_U,E_O,W_O,D_O,R_O,S_O,H,H_G,H_U,H_O,C,C_G,C_U,C_O,P,P_G,P_U,P_O,N,N_G,N_U,N_O,
$$
then they expose the same $\RealUp$ seal boundary. The shared surface carries no quotient stream, selected host limit, host equality, choice principle, ambient completeness theorem, open-cover compactness principle, hidden family limit, or direct $\RealUp$ bypass.
\end{theorem}
\begin{proof}
Begin with root extraction and tail-window totality. Root extraction confines every public read of $W$ to $S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N$, and tail-window totality forces $\sigma,\mu,\lambda$ to be consumed before any located-trap, synchronizer, observation-budget, or $\RealUp$ seal read can inspect $Q$.

Next apply grid budget precedence. The grid rows $B,L,K,T$ occur before the seal row on the same root route, while $S_G,R_G,E_G$ are the displayed StreamName, RegSeqRat, and Real-seal faces of that route. Thus the grid packet cannot alter the seal boundary without altering a displayed row.

Now use the uniform criterion handoff. The packet $U$ reads the same finite windows, shared modulus, dyadic tolerance, tail ledger, and seal handoff already exposed by the bounded-source and grid routes, so a public criterion read preserving those rows preserves the same seal-facing boundary.

Apply the observation-budget grid pullback and the criterion-grid-synchronizer correspondence. These identify the observation request, window, dyadic, regular-handoff, seal, synchronizer, transport, continuation, provenance, and naming rows as one shared pullback surface before the $\RealUp$ seal is public.

Finally use Real-seal consumer exhaustion. A downstream seal consumer has only the displayed witness, grid, criterion, synchronizer, observation-budget, transport, continuation, provenance, and naming rows listed above. Therefore two reads that preserve those rows determine the same public $\RealUp$ seal boundary, and the excluded quotient-stream, selected-limit, host-equality, choice, completeness, compactness, and bypass routes have no carrier coordinate.
\end{proof}

\begin{theorem}[Bounded monotone Cauchy witness grid selector exactness]
\label{thm:bounded-monotone-cauchy-witness-grid-selector-exactness}
Let $W=(S,F,\sigma,\mu,\lambda,I,Q,H,C,P,N)$ be an accepted $\BoundedMonotoneCauchyWitnessUp$ packet. Let
$$
G=(B,L,K,T,S_G,R_G,E_G,H_G,C_G,P_G,N_G)
$$
be an accepted $\RealCauchyWitnessGridUp$ packet, let
$$
U=(I_U,W_U,M_U,Q_U,T_U,E_U,H_U,C_U,P_U,N_U)
$$
be an accepted $\UniformCauchyCriterionUp$ packet, let $Y$ be an accepted $\CauchySealBudgetSynchronizerUp$ packet, and let
$$
O=(E_O,W_O,D_O,R_O,S_O,H_O,C_O,P_O,N_O)
$$
be an accepted $\RealObservationBudgetUp$ packet. Suppose these packets read the same finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ ledgers, $\RegSeqRatUp$ regular readbacks, and $\RealUp$ seal row displayed by the root route of $W$.

Then the public selector route from $W,G,U,Y,O$ is exact. Any two selector-facing reads that preserve the bounded-source rows $S,F,\sigma,\mu,\lambda,I,Q$, the grid-budget rows $B,L,K,T,S_G,R_G,E_G$, the uniform-criterion rows $I_U,W_U,M_U,Q_U,T_U,E_U$, the synchronizer seal-budget rows of $Y$, the observation-budget rows $E_O,W_O,D_O,R_O,S_O$, the componentwise transport rows $H,H_G,H_U,H_O$, the displayed continuation rows $C,C_G,C_U,C_O$, the provenance rows $P,P_G,P_U,P_O$, and the local NameCert rows $N,N_G,N_U,N_O$ expose the same selector-facing $\RealUp$ seal boundary.

The exact selector surface has no coordinate for quotient streams, selected host limits, host real equality, choice selectors, ambient completeness, open-cover compactness, hidden family limits, or a direct $\RealUp$ bypass.
\end{theorem}
\begin{proof}
First extract the root route. Root extraction and root tail-window totality force every selector-facing read of $W$ through the displayed bounded source, regular readback, finite window, modulus, dyadic ledger, located trap, seal row, transport, continuation, provenance, and local naming rows.

Next attach the grid route. Grid budget precedence and grid route compatibility keep $G$ on the same finite-window, dyadic-ledger, regular-readback, and seal boundary as $W$. The grid rows therefore refine the selector budget on the displayed route rather than adding a second completion stream.

Now add the criterion, synchronizer, and observation faces. The observation-budget grid pullback identifies the observation rows with the same window, ledger, readback, and seal surface, while the criterion-grid-synchronizer correspondence places the uniform criterion and synchronizer rows on that shared surface before the seal is public.

Finally apply root Real-seal determinacy. Once the bounded-source, grid-budget, uniform-criterion, synchronizer, observation-budget, transport, continuation, provenance, and NameCert rows are preserved, any two public selector reads expose the same $\RealUp$ seal boundary. Since the preceding route inventory contains no quotient, selected-limit, host-equality, choice, completeness, compactness, hidden-family, or bypass coordinate, no such data can enter the selector.
\end{proof}
