\section{Consumer threshold surface}
\label{sec:innerproduct-consumer-threshold-surface}

\begin{definition}[InnerProduct consumer threshold source]
\label{def:innerproduct-consumer-threshold-source}
The $\InnerProductUp$ consumer threshold source is the NameCert-facing
package through which later certificates read inner-product data. It has the
following ten fields:
\begin{enumerate}
  \item traditional target: inner-product geometry over a vector space;
  \item BEDC source: the displayed $\NameCert_{\VecSpaceUp}$ source, its
  retained scalar and field rows, and the $\NameCert$ ledger discipline;
  \item vector carrier: a predicate
  $C_V:\mathsf{BHist}\to\mathsf{Prop}$;
  \item vector classifier: the displayed classifier $\sim_V$ on carried
  vector histories;
  \item scalar endpoint classifier: the retained scalar classifier on all
  scalar endpoints read by the form;
  \item form row: the scalar-valued endpoint row
  $\langle-,-\rangle_{\InnerProductUp}:C_V\times C_V\to C_{\mathsf{scal}}$;
  \item law rows: conjugate symmetry, sesquilinearity, positivity, and form
  endpoint transport;
  \item ledger rows: scalar endpoints, $\hsame$ transport, optional $\Cont$
  route histories, and the orthogonality rows visible to consumers;
  \item source factorization: every carrier, classifier, scalar, form, law,
  transport, and ledger projection factors through
  \autoref{def:innerproduct-bhist-carrier},
  \autoref{def:innerproduct-bhist-source}, and
  \autoref{def:innerproduct-root-threshold-source};
  \item exclusion boundary: Banach completeness, topology, host Hilbert
  carriers, and Cauchy-limit selectors are not fields of this source.
\end{enumerate}
Thus $\HilbertUp$, $\FourierUp$, $\RiemannianMetricUp$, and $\RootSystemUp$
receive a single inner-product threshold package rather than separate echoes
of the root rows.
\end{definition}

\begin{theorem}[InnerProduct consumer carrier and form scope]
\label{thm:innerproduct-consumer-carrier-form-scope}
Every carrier, classifier, scalar endpoint, and form read from the consumer
threshold source of \autoref{def:innerproduct-consumer-threshold-source}
factors through the $\mathsf{BHist}$ carrier of
\autoref{def:innerproduct-bhist-carrier}, the source rows of
\autoref{def:innerproduct-bhist-source}, and the root threshold source of
\autoref{def:innerproduct-root-threshold-source}. No consumer can read a
second vector carrier, a second scalar endpoint source, or a host
inner-product-space form from this package.
\end{theorem}
\begin{proof}
Start with the carrier field. By
\autoref{thm:innerproduct-bhist-carrier-row}, the public carrier row is the
displayed $\VecSpaceUp$ BHist carrier $C_V$ together with the scalar-valued
form endpoint row. The consumer threshold source names this same row as its
vector carrier and does not list any other point carrier.

Next read the scalar and form fields from
\autoref{def:innerproduct-bhist-source}. The form endpoint lands in the
retained scalar history carrier and is classified by the retained scalar
classifier. By
\autoref{thm:innerproduct-root-vecspace-scalar-exposure}, these vector and
scalar projections exhaust the vector-scalar part of the root surface.

Finally apply \autoref{thm:innerproduct-root-threshold-form-exactness}. The
form law rows exposed at the consumer boundary are the form, law, and
transport rows of \autoref{def:innerproduct-root-threshold-source}. Since the
consumer threshold source is defined by projecting those root threshold rows,
every consumer carrier or form read factors through the three cited source
objects.
\end{proof}

\begin{theorem}[InnerProduct consumer positivity and orthogonality scope]
\label{thm:innerproduct-consumer-positive-orthogonality-scope}
The positivity and orthogonality data exported by
\autoref{def:innerproduct-consumer-threshold-source} are exactly the
positive-definite scalar-zero classification row and the orthogonality closure
rows built from \autoref{def:innerproduct-orthogonality-row}. They add no
host positivity predicate and no independent Hilbert-space orthogonality
relation.
\end{theorem}
\begin{proof}
For positivity, use
\autoref{thm:innerproduct-positive-definite-obligation}. The diagonal
self-value $\langle x,x\rangle_{\InnerProductUp}$ is classified as the scalar
zero endpoint exactly when $x$ is classified with the displayed vector zero
row. This is the positive row exposed by
\autoref{thm:innerproduct-root-threshold-form-exactness}.

For orthogonality, unfold
\autoref{def:innerproduct-orthogonality-row}. The statement $x\perp_I y$ is
the scalar-zero classification of
$\langle x,y\rangle_{\InnerProductUp}$. The zero-left, zero-right, and
transport rows are
\autoref{thm:innerproduct-zero-left-orthogonal-row},
\autoref{thm:innerproduct-zero-right-orthogonal-row}, and
\autoref{thm:innerproduct-orthogonality-transport-row}.

The closure rows available to downstream consumers are the rows of the
orthogonality closure surface:
\autoref{thm:innerproduct-orthogonality-symmetry-row},
\autoref{thm:innerproduct-orthogonal-additivity-row},
\autoref{thm:innerproduct-orthogonality-right-scalar-action-closure}, and
\autoref{thm:innerproduct-orthogonal-additive-inverse-closure}. Each row is
proved from the scalar-zero definition of orthogonality and the displayed
inner-product law rows. Therefore the consumer threshold exports exactly
scalar-zero positivity and the orthogonality rows derived from it.
\end{proof}

\begin{theorem}[InnerProduct consumer Hilbert threshold package]
\label{thm:innerproduct-consumer-hilbert-threshold-package}
The $\HilbertUp$ certificate consumes from
\autoref{def:innerproduct-consumer-threshold-source} only the
inner-product-side threshold rows: vector carrier and classifier, retained
scalar endpoints, the form row, conjugate symmetry, sesquilinearity,
positivity, form transport, orthogonality, and ledger provenance. Its Banach
metric, completeness row, topology, and Cauchy-limit selector remain external.
The $\FourierUp$, $\RiemannianMetricUp$, and $\RootSystemUp$ consumers are
restricted to the same form, law, transport, and ledger rows.
\end{theorem}
\begin{proof}
For the Hilbert input, apply
\autoref{thm:innerproduct-root-threshold-orthogonality-consumption}. It
states that the Hilbert-facing geometric data are the scalar-valued form rows
and the orthogonality row derived from them, while Banach metric,
completeness, and Cauchy-limit rows come from a separate dependency.

For the named non-Hilbert consumers, apply
\autoref{thm:innerproduct-root-threshold-downstream-coverage}. It restricts
$\FourierUp$, $\RiemannianMetricUp$, and $\RootSystemUp$ to the vector,
scalar, form, law, transport, orthogonality, and ledger rows of the same root
threshold source.

The consumer threshold source is the single package that exposes those root
threshold rows to downstream certificates. Its exclusion boundary lists no
Banach completeness, topology, host Hilbert carrier, or Cauchy-limit selector.
Hence every named consumer reads only the inner-product threshold rows, and
all completeness or topology structure remains outside
$\NameCert_{\InnerProductUp}$.
\end{proof}
