\begin{theorem}[ApophaticName root refusal boundary exhaustion]
\label{thm:apophatic-name-root-refusal-boundary-exhaustion}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
every root conversion attempt from the named externality into internal content is exhausted by the displayed refusal gate $G$, refusal ledger $L$, and the structural rows $S,R,H,C,P,N$. The attempt is either a socket request carried by $S$ and $R$, a refusal-gate read classified by $G$, a barred conversion recorded by $L$, or a replay through $H,C,P,N$ that preserves the same boundary refusal. There is no additional root route to a generated witness, quotient representative, host object, hidden theorem, supplied external object, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_root\_refusal\_boundary\_exhaustion}
\begin{proof}
Start with the carrier of \autoref{def:apophatic-name-carrier}. It displays the accepted packet as exactly the eight rows $S,R,G,L,H,C,P,N$.

Apply the obligation surface of \autoref{thm:apophatic-name-obligation-surface}. It records carrier admission, classifier stability, ledger exactness, continuation provenance, and non-escape as the local NameCert obligations for this packet.

Next use the root socket-gate factorization, \autoref{thm:apophatic-name-root-socket-gate-factorization}, together with root refusal-ledger exhaustion, \autoref{thm:apophatic-name-root-refusal-ledger-exhaustion}. These force a root read through the socket, requested supply-shape row, refusal gate, and ledger before any structural replay row is consumed.

Finally apply the non-escape certificate, \autoref{thm:apophatic-name-non-escape-certificate}. Since the carrier has no coordinate for the listed internal objects and every conversion attempt has already been routed through $G$ and $L$, the displayed refusal gate and ledger exhaust the root boundary.
\end{proof}

\begin{theorem}[ApophaticName supply-shape noninternalization]
\label{thm:apophatic-name-supply-shape-noninternalization}
For every accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, the requested supply-shape row $R$ remains a boundary request. It may be exposed to the socket row $S$, classified by the refusal gate $G$, recorded in the refusal ledger $L$, transported through $H$, replayed through $C$, authenticated by $P$, and named by $N$, but it cannot be internalized as a generated witness, quotient representative, host object, hidden theorem, supplied external object, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_supply\_shape\_noninternalization}
\begin{proof}
Project the carrier and the refusal ledger. The carrier \autoref{def:apophatic-name-carrier} gives $R$ only as the requested supply-shape row, while \autoref{thm:apophatic-name-refusal-ledger} records the barred conversions from requested supply into internal content.

Use the supply-shape refusal exactness theorem, \autoref{thm:apophatic-name-supply-shape-refusal-exactness}. It identifies reads of the requested supply shape with the visible boundary row rather than with a generated or host-side object.

Now add the root boundary. By \autoref{thm:apophatic-name-root-refusal-boundary-exhaustion}, any root attempt to turn $R$ into internal content has already been classified by $G$ and refused by $L$.

The non-escape certificate \autoref{thm:apophatic-name-non-escape-certificate} removes the remaining alternatives. Thus $R$ is preserved as a boundary request through $S,G,L,H,C,P,N$ and is not an internal witness, representative, object, theorem, supplied externality, or closure principle.
\end{proof}

\begin{theorem}[ApophaticName downstream socket ledger factorization]
\label{thm:apophatic-name-downstream-socket-ledger-factorization}
Every downstream socket consumer that cites $\ApophaticNameUp$ factors through the finite packet
$$
S,R,G,L,H,C,P,N
$$
and through the sibling $\ApophaticSocketUp$ and $\ApophaticGateQuestionUp$ socket and gate surfaces before the citation reaches the ApophaticNameUp boundary. The citation therefore consumes a ledgered refusal interface, not an unrecorded supply channel or hidden closure object.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_downstream\_socket\_ledger\_factorization}
\begin{proof}
Begin with downstream socket route exactness, \autoref{thm:apophatic-name-downstream-socket-route-exactness}. It sends downstream reads through $S,R,G,L,H,C,P,N$ and leaves no route outside the displayed packet.

Next use root downstream socket non-escape, \autoref{thm:apophatic-name-root-downstream-socket-nonescape}. It permits public citation of the sibling socket and gate-question boundaries while keeping the consumer inside the same refusal packet.

Apply the root socket-gate factorization, \autoref{thm:apophatic-name-root-socket-gate-factorization}. This places the socket row $S$, requested supply-shape row $R$, refusal gate $G$, and refusal ledger $L$ before the transport, continuation, provenance, and local naming rows.

Finally combine refusal boundary exhaustion and supply-shape noninternalization from \autoref{thm:apophatic-name-root-refusal-boundary-exhaustion} and \autoref{thm:apophatic-name-supply-shape-noninternalization}. The downstream consumer may cite the sibling surfaces and the ApophaticNameUp boundary only through the ledgered packet, so it cannot obtain an unrecorded supply channel, generated witness, host object, quotient representative, hidden theorem, or closure principle.
\end{proof}

\begin{theorem}[ApophaticName root refusal terminal nonpromotion]
\label{thm:apophatic-name-root-refusal-terminal-nonpromotion}
Let $A=(S,R,G,L,H,C,P,N)$ be an accepted $\ApophaticNameUp$ packet. Any terminal root conversion attempt that has already passed through the downstream socket ledger remains a refusal-boundary read of $S,R,G,L,H,C,P,N$. The requested supply-shape row $R$ cannot be promoted into an internal generated witness, quotient representative, host object, hidden theorem, supplied external object, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_root\_refusal\_terminal\_nonpromotion}
\begin{proof}
Begin with downstream socket ledger factorization, \autoref{thm:apophatic-name-downstream-socket-ledger-factorization}. A terminal downstream consumer citing the ApophaticNameUp boundary must pass through $S,R,G,L,H,C,P,N$ and the sibling socket and gate surfaces before the citation reaches the refusal packet.

Apply root refusal boundary exhaustion and supply-shape noninternalization, \autoref{thm:apophatic-name-root-refusal-boundary-exhaustion} and \autoref{thm:apophatic-name-supply-shape-noninternalization}. These results classify every root conversion attempt by $G$, record the barred conversion in $L$, and keep the requested supply-shape row $R$ as boundary data.

Finally use the non-escape certificate, \autoref{thm:apophatic-name-non-escape-certificate}. Since the carrier has no coordinate for generated witnesses, quotient representatives, host objects, hidden theorems, supplied external objects, or closure principles, passing through the downstream socket ledger cannot turn the refusal boundary into any of those internal objects.
\end{proof}

\begin{corollary}[ApophaticName root refusal boundary strict obstruction]
\label{cor:apophatic-name-root-refusal-boundary-strict-obstruction}
Let $A=(S,R,G,L,H,C,P,N)$ be an accepted $\ApophaticNameUp$ packet. Any consumer-facing use of the root refusal boundary as an obstruction is strictly local to the displayed finite route
$$
S,R,G,L,H,C,P,N.
$$
It blocks exactly the converse or reuse attempt that would reread the named externality as a generated witness, quotient representative, host object, hidden theorem, supplied external object, closure principle, unrecorded supply channel, or hidden external validation. It cannot be reinterpreted as a global impossibility claim, a host theorem, an ambient countermodel, or an external validation result outside the accepted packet.
\end{corollary}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_root\_refusal\_boundary\_strict\_obstruction}
\begin{proof}
Begin with root refusal boundary exhaustion, \autoref{thm:apophatic-name-root-refusal-boundary-exhaustion}. It classifies every root conversion attempt into the displayed alternatives: a socket request through $S$ and $R$, a refusal-gate read classified by $G$, a barred conversion recorded by $L$, or a replay through $H,C,P,N$ that preserves the same boundary refusal. The same theorem also excludes any additional root route to a generated witness, quotient representative, host object, hidden theorem, supplied external object, or closure principle.

Now apply downstream socket ledger factorization, \autoref{thm:apophatic-name-downstream-socket-ledger-factorization}. Any downstream consumer that cites the $\ApophaticNameUp$ boundary must first factor through the finite packet $S,R,G,L,H,C,P,N$ and through the sibling socket and gate surfaces before the citation reaches the boundary. Thus a consumer-facing obstruction has no coordinate except the displayed socket, request, refusal, ledger, transport, continuation, provenance, and local naming rows.

The strictness is the separation between the permitted forward citation and the barred converse. In the permitted direction, the consumer may cite the ledgered refusal interface. In the barred converse or reuse direction, the consumer tries to turn that interface into supplied content, a generated witness, a quotient representative, a host object, a hidden theorem, a closure principle, an unrecorded supply channel, or hidden external validation. Root exhaustion sends that attempt back to $G$ and $L$, and downstream factorization keeps every public use inside the same packet.

Therefore the obstruction is not a theorem about all ambient hosts, not a hidden host proof, not an external countermodel, and not a validation source outside $A$. It is exactly the local refusal-boundary obstruction carried by $S,R,G,L,H,C,P,N$ against the named converse or reuse route.
\end{proof}
