\begin{theorem}[ApophaticName refusal ledger exactness]
\label{thm:apophatic-name-refusal-ledger-exactness}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, the refusal ledger $L$ is exact for downstream root-unblock use: it records precisely the permitted reads of $S$ and $R$, the refusal decision carried by $G$, and the transports and replays through $H,C,P,N$. No consumer can add a further ledger row that converts the socket into a generated witness, quotient representative, hidden theorem, host object, supplied external dependency, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_refusal\_ledger\_exactness}
\begin{proof}
Begin with \autoref{thm:apophatic-name-refusal-ledger}. It identifies $L$ as the ledger for the permitted socket and request reads and for the barred conversions.

Use \autoref{thm:apophatic-name-ledger-nonescape}. Every downstream read already factors through the displayed refusal ledger, so a consumer has no unledgered path to hidden proof, host equality, quotient representative, generated witness, or closure principle.

Apply the non-escape certificate and root-unblock refusal boundary, \autoref{thm:apophatic-name-non-escape-certificate} and \autoref{thm:apophatic-name-root-unblock-refusal-boundary}. They confine downstream root-unblock use to $S,R,G,L,H,C,P,N$.

Finally cite the externality handoff theorem, \autoref{thm:apophatic-name-externality-handoff}. The only handoff object is the same finite refusal packet, so exactness of $L$ cannot be extended into a supplied object or closure principle.
\end{proof}

\begin{theorem}[ApophaticName boundary request image row]
\label{thm:apophatic-name-boundary-request-image-row}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, every accepted ApophaticName consumer read of the boundary request has image inside the displayed finite tuple $S,R,G,L,H,C,P,N$. The image row may cite the socket, requested supply shape, refusal gate, refusal ledger, componentwise transport, continuation route, package provenance, or local $\NameCert_{\ApophaticNameUp}$ component, and it cannot cite a supplied object, quotient representative, hidden theorem, host-side realization, generated witness, or closure principle outside that tuple.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_boundary\_request\_image\_row}
\begin{proof}
Project the carrier in \autoref{def:apophatic-name-carrier}. The accepted packet has exactly the socket, request, refusal gate, ledger, transport, continuation, provenance, and local naming coordinates.

Apply the refusal ledger and ledger exactness rows, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-refusal-ledger-exactness}. They identify the permitted reads of $S$ and $R$, the decision carried by $G$, and the replay rows through $L,H,C,P,N$.

Finally use the sibling socket and gate boundaries already binding the chapter, \autoref{thm:apophatic-name-socket-carrier}, \autoref{thm:apophatic-name-root-unblock-refusal-boundary}, and \autoref{thm:apophatic-name-socket-request-gate-factorization}. These boundaries keep every accepted consumer read inside the finite refusal tuple rather than an internal object or host-side witness.
\end{proof}

\begin{theorem}[ApophaticName refusal readback row]
\label{thm:apophatic-name-refusal-readback-row}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, every accepted image-row read has a readback to the corresponding finite $\BHist$ component: $S$ reads back the socket, $R$ the request, $G$ the refusal decision, $L$ the refusal ledger, $H$ the componentwise transport, $C$ the route, $P$ the provenance, and $N$ the local $\NameCert_{\ApophaticNameUp}$ component. The readback does not convert the socket into an internal object or supplied dependency.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_refusal\_readback\_row}
\begin{proof}
Start with the carrier of \autoref{def:apophatic-name-carrier}. Each displayed coordinate of $S,R,G,L,H,C,P,N$ is finite $\BHist$ data or a public row over that data.

Use the refusal ledger theorem and exactness theorem, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-refusal-ledger-exactness}. They pair each permitted consumer read with the row that records it, so a read of the socket, request, gate, ledger, transport, route, provenance, or local name reads back to the corresponding component.

The socket and gate boundaries, \autoref{thm:apophatic-name-socket-carrier}, \autoref{thm:apophatic-name-root-unblock-refusal-boundary}, and \autoref{thm:apophatic-name-boundary-request-image-row}, then exclude every readback path that would replace the displayed component by supplied content. Thus readback recovers the finite row and nothing beyond it.
\end{proof}

\begin{theorem}[ApophaticName boundary request tuple totality]
\label{thm:apophatic-name-boundary-request-tuple-totality}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, every accepted boundary-request read has both its image row and its readback row inside the same displayed tuple. Componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\ApophaticNameUp}$ row exhaust the consumer surface, so the read cannot escape to a supplied object, hidden theorem, quotient representative, generated witness, host datum, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_boundary\_request\_tuple\_totality}
\begin{proof}
Begin with the image and readback rows, \autoref{thm:apophatic-name-boundary-request-image-row} and \autoref{thm:apophatic-name-refusal-readback-row}. The image row confines each accepted boundary-request read to $S,R,G,L,H,C,P,N$, and the readback row returns each accepted image read to the corresponding finite $\BHist$ component of that tuple.

Apply the componentwise transport row, \autoref{thm:apophatic-name-componentwise-namecert-transport-row}. It says that the local $\NameCert_{\ApophaticNameUp}$ component replays exactly those image and readback rows over the same displayed coordinates under $\hsame$ transport.

It remains to account for the consumer surface. The continuation row $C$ supplies only replay through the displayed boundary-request tuple, the provenance row $P$ names the same finite packet, and the local naming row $N$ exports no additional object. Thus the tuple already contains every accepted image, readback, transport, replay, provenance, and naming row.

The no-supplied-object conclusion follows because no coordinate of $A$ stores a supplied object, hidden theorem, quotient representative, generated witness, host datum, or closure principle. Any consumer request for such content therefore leaves the accepted tuple surface and is rejected at the refusal boundary.
\end{proof}

\begin{theorem}[ApophaticName refusal tuple bridge scope]
\label{thm:apophatic-name-refusal-tuple-bridge-scope}
Any bridge-facing consumer of an accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N)
$$
must preserve the image row, readback row, componentwise NameCert transport, refusal ledger, continuation route, package provenance, and local naming row together. The bridge scope exports no supplied object, hidden theorem, quotient representative, host datum, generated witness, or closure principle.
\end{theorem}
\begin{proof}
Begin with the image and readback rows, \autoref{thm:apophatic-name-boundary-request-image-row} and \autoref{thm:apophatic-name-refusal-readback-row}. They place every accepted boundary-request image inside $S,R,G,L,H,C,P,N$ and return each accepted read to the corresponding finite $\BHist$ component.

Use boundary-request tuple totality, \autoref{thm:apophatic-name-boundary-request-tuple-totality}. The continuation route, package provenance, and local naming row already exhaust the consumer surface, so a bridge-facing consumer receives the same finite refusal tuple rather than a separate boundary object.

Apply componentwise NameCert transport, \autoref{thm:apophatic-name-componentwise-namecert-transport-row}. It replays the image and readback rows over the same displayed coordinates under $\hsame$ transport, preserving the refusal ledger, continuation route, package provenance, and local naming row together.

Since the accepted tuple has no coordinate for a supplied object, hidden theorem, quotient representative, host datum, generated witness, or closure principle, the bridge scope cannot export any such object. It exports only the displayed refusal tuple and its componentwise transport route.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_refusal\_tuple\_bridge\_scope}

\begin{theorem}[ApophaticName componentwise NameCert transport row]
\label{thm:apophatic-name-componentwise-namecert-transport-row}
For accepted $\ApophaticNameUp$ packets transported along the displayed componentwise $\hsame$ row $H$, the local $\NameCert_{\ApophaticNameUp}$ component replays the image and readback rows componentwise over $S,R,G,L,H,C,P,N$. The transport keeps the socket a public boundary component and never converts it into an internal object, supplied dependency, quotient representative, hidden theorem, host datum, or closure principle.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_componentwise\_namecert\_transport\_row}
\begin{proof}
Project the carrier from \autoref{def:apophatic-name-carrier}. The transport row $H$ is one coordinate of the same accepted packet as the socket, request, gate, ledger, continuation, provenance, and local NameCert rows.

Apply the refusal ledger and exactness rows, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-refusal-ledger-exactness}. They make the rows that are eligible for transport exactly the finite refusal tuple, with no hidden coordinate for supplied content.

Now use the image and readback rows, \autoref{thm:apophatic-name-boundary-request-image-row} and \autoref{thm:apophatic-name-refusal-readback-row}. The local NameCert transport can replay only those componentwise rows, because each consumer image and each readback has already been confined to $S,R,G,L,H,C,P,N$.

Finally cite the sibling socket and gate boundaries, \autoref{thm:apophatic-name-root-unblock-refusal-boundary} and \autoref{thm:apophatic-name-socket-request-gate-factorization}. They keep the transported socket on the public refusal boundary, so the transport is a replay of the displayed rows rather than an internalization of the socket.
\end{proof}

\begin{theorem}[ApophaticName classifier stability]
\label{thm:apophatic-name-classifier-stability}
Accepted $\ApophaticNameUp$ packets transported componentwise along the displayed $\hsame$ rows preserve the socket-name row, requested supply shape, refusal gate, refusal ledger, continuation routes, package provenance, and local $\NameCert_{\ApophaticNameUp}$ row. For a packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the transported classifier still reads only $S,R,G,L,H,C,P,N$ and cannot gain a supplied object, axiom, quotient representative, hidden theorem, or host-side realization.
\end{theorem}
\begin{proof}
Project the carrier tuple $A=(S,R,G,L,H,C,P,N)$ from \autoref{def:apophatic-name-carrier}. The classifier-facing coordinates are exactly the socket, request, refusal gate, ledger, transport, continuation, package, and naming rows.

Use the refusal ledger of \autoref{thm:apophatic-name-refusal-ledger}. It records the permitted socket reads and the barred conversions from requested supply to internal object, axiom, quotient representative, hidden theorem, or host-side datum.

Apply the obligation surface of \autoref{thm:apophatic-name-obligation-surface}. Its classifier-stability, ledger-exactness, continuation, package, and non-escape rows exhaust the local NameCert obligations for the same tuple.

Componentwise $\hsame$ transport can therefore move only the displayed coordinates. Since $C$ and $P$ preserve the continuation and package provenance rows, and since $N$ remains the local naming row for that transported packet, no additional coordinate appears in which a supplied object, axiom, quotient representative, hidden theorem, or host-side realization could be stored.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_classifier\_stability}

\begin{theorem}[ApophaticName source-refusal totality]
\label{thm:apophatic-name-source-refusal-totality}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the concrete socket row $S$, requested supply-shape row $R$, refusal gate $G$, refusal ledger $L$, componentwise $\hsame$ row $H$, $\Cont$ route row $C$, $\Pkg$ provenance row $P$, and local $\NameCert_{\ApophaticNameUp}$ row $N$ exhaust the source-refusal surface over $\BHist$. No consumer can ask the packet for an internal object, assumed proposition, quotient representative, hidden theorem, or host-side datum without first encountering the refusal ledger.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:apophatic-name-carrier}. Its concrete packet rows are exactly $S,R,G,L,H,C,P,N$, and each row is finite $\BHist$ data.

Apply the refusal ledger of \autoref{thm:apophatic-name-refusal-ledger}. It records the permitted socket and request reads together with the barred conversions from a named externality to internal content.

Use classifier stability from \autoref{thm:apophatic-name-classifier-stability}. Componentwise $\hsame$ transport preserves the same socket, request, gate, ledger, continuation, package, and local naming rows, so no new source coordinate appears during transport.

Finally apply non-escape through \autoref{thm:apophatic-name-non-escape-certificate}. The displayed $\Cont$, $\Pkg$, and $\NameCert$ rows export the refusal surface but do not install an internal witness behind the socket.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_source\_refusal\_totality}

\begin{theorem}[ApophaticName public boundary package]\label{thm:apophatic-name-public-boundary-package}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the public root-unblock package exposed over $\BHist$ is exactly the socket row $S$, request row $R$, refusal gate $G$, refusal ledger $L$, componentwise $\hsame$ row $H$, continuation route $C$, package provenance $P$, and local $\NameCert_{\ApophaticNameUp}$ row $N$. The package exports no supplied dependency, internal object, assumed proposition, quotient representative, hidden theorem, host object, or closure principle beyond these rows.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:apophatic-name-carrier}. Its accepted packet has exactly the displayed rows $S,R,G,L,H,C,P,N$, with no extra coordinate in which supplied content could be stored.

Use the refusal ledger and source-refusal totality, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-source-refusal-totality}. They send every requested supply read through the gate and ledger before a consumer can ask for internal content.

Apply the non-escape certificate, \autoref{thm:apophatic-name-non-escape-certificate}. It rules out converting the public packet into an axiom, quotient representative, hidden theorem, host-side datum, or closure principle, so the public root-unblock package is exhausted by the eight displayed rows.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_public\_boundary\_package}

\begin{theorem}[ApophaticName socket citation scope]\label{thm:apophatic-name-socket-citation-scope}
Every downstream citation of an $\ApophaticNameUp$ socket must retain the request row $R$, refusal gate $G$, refusal ledger $L$, continuation route $C$, package provenance $P$, and local $\NameCert_{\ApophaticNameUp}$ row $N$ together with the socket row $S$ and transport row $H$. A citation that drops any of these rows is not a citation of the accepted public package.
\end{theorem}
\begin{proof}
Start with the socket carrier and public boundary package, \autoref{def:apophatic-name-carrier} and \autoref{thm:apophatic-name-public-boundary-package}. They identify the cited public object with the finite packet $S,R,G,L,H,C,P,N$.

Apply source-refusal totality from \autoref{thm:apophatic-name-source-refusal-totality}. The source side is not merely a socket name: each accepted request is paired with the refusal gate and ledger that block conversion into supplied content.

Finally use the downstream non-escape and provenance rows, \autoref{thm:apophatic-name-non-escape-certificate} and \autoref{thm:apophatic-name-externality-handoff}. They force socket citations to keep the continuation route, package provenance, and local naming row that make the refusal auditable at the cited site.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_socket\_citation\_scope}

\begin{theorem}[ApophaticName refusal audit package]\label{thm:apophatic-name-refusal-audit-package}
The audit-facing refusal package of an accepted $\ApophaticNameUp$ packet is exhausted by the finite rows
$$
S,R,G,L,H,C,P,N.
$$
It cannot be converted by an auditor into an axiom, quotient representative, hidden theorem, host object, supplied dependency, or closure principle.
\end{theorem}
\begin{proof}
Read the audit package through the carrier and refusal ledger, \autoref{def:apophatic-name-carrier} and \autoref{thm:apophatic-name-refusal-ledger}. The ledger records permitted socket and request reads and records the blocked conversions at the same finite packet.

Use the socket citation scope from \autoref{thm:apophatic-name-socket-citation-scope}. Any downstream audit citation still carries the request, gate, ledger, route, provenance, and local naming rows, so the auditor receives the same finite surface.

Apply source-refusal totality and the non-escape certificate, \autoref{thm:apophatic-name-source-refusal-totality} and \autoref{thm:apophatic-name-non-escape-certificate}. These rule out every route from the audit package to an internal witness or host-side closure object, leaving only the displayed refusal rows.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_refusal\_audit\_package}

\begin{theorem}[ApophaticName refusal transport totality]
\label{thm:apophatic-name-refusal-transport-totality}
For accepted $\ApophaticNameUp$ packets
$$
A=(S,R,G,L,H,C,P,N)
$$
and
$$
A'=(S',R',G',L',H',C',P',N')
$$
whose displayed rows are related componentwise by the $\hsame$ transports, refusal transport preserves exactly the socket row, requested supply row, refusal gate, refusal ledger, transport row, continuation route, package provenance, and local naming row. The transported packet cannot create supplied content, an internal witness, an assumed proposition, a quotient representative, a hidden theorem, or a host object.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_refusal\_transport\_totality}
\begin{proof}
Project both carriers through \autoref{def:apophatic-name-carrier}. The only coordinates available before and after transport are $S,R,G,L,H,C,P,N$ and $S',R',G',L',H',C',P',N'$.

Use the refusal ledger and ledger nonescape rows, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-ledger-nonescape}. They keep every permitted read on the socket, request, gate, and ledger rows, and they bar every conversion into supplied or host-side content.

Apply source-refusal totality from \autoref{thm:apophatic-name-source-refusal-totality}. Since the source-refusal surface is already exhausted by $S,R,G,L,H,C,P,N$, componentwise transport can only rename and replay those same rows through $H,C,P,N$.

The sibling socket and gate references preserve the same boundary shape. \autoref{thm:apophatic-socket-consumer-surface} keeps the socket readable only as socket data, while \autoref{thm:apophatic-gate-question-visible-socket-nonescape} keeps the gate attached to a visible refusal. Hence the transported packet remains exactly a refusal packet and has no coordinate in which supplied content can appear.
\end{proof}

\begin{theorem}[ApophaticName socket-gate route exhaustion]
\label{thm:apophatic-name-socket-gate-route-exhaustion}
Every socket read of an accepted $\ApophaticNameUp$ packet factors through the socket row $S$, requested supply row $R$, refusal gate $G$, refusal ledger $L$, componentwise transport $H$, continuation route $C$, package provenance $P$, and local $\NameCert_{\ApophaticNameUp}$ row $N$. No socket consumer can bypass this route to read the named externality as supplied content, an internal object, a quotient representative, a hidden theorem, a host datum, or a closure principle.
\end{theorem}
\begin{proof}
Begin with the socket carrier and socket refusal rows, \autoref{thm:apophatic-name-socket-carrier} and \autoref{thm:apophatic-name-socket-refusal}. They identify the socket-facing surface as the finite packet $S,R,G,L,H,C,P,N$ rather than an internal witness.

Use gate-source compatibility and the sibling gate boundary. \autoref{thm:apophatic-name-gate-source-compatibility} keeps $S,R,G,L$ as one source surface, and \autoref{thm:apophatic-gate-question-visible-socket-nonescape} prevents the gate from becoming an admitted supply.

Now apply refusal transport totality from \autoref{thm:apophatic-name-refusal-transport-totality}. Any socket read transported downstream remains on the same refusal rows and is replayed only through $H,C,P,N$.

Finally use source-refusal totality and downstream refusal-ledger exhaustion, \autoref{thm:apophatic-name-source-refusal-totality} and \autoref{thm:apophaticname-downstream-refusal-ledger-exhaustion}. These exhaust the requested supply row, refusal ledger, continuation route, provenance, and local naming rows, leaving no socket route outside the displayed packet.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_socket\_gate\_route\_exhaustion}

\begin{theorem}[ApophaticName downstream boundary consumption]
\label{thm:apophatic-name-downstream-boundary-consumption}
Downstream consumers may consume the named externality of an accepted $\ApophaticNameUp$ packet only as the finite refusal packet $S,R,G,L,H,C,P,N$. The boundary is not consumable as an internal witness, quotient representative, hidden theorem, host object, supplied dependency, assumed proposition, or closure principle.
\end{theorem}
\begin{proof}
Start from externality handoff, \autoref{thm:apophatic-name-externality-handoff}. The handoff object is already the finite refusal packet, so downstream citation begins with $S,R,G,L,H,C,P,N$ rather than with supplied content.

Apply boundary citation exhaustion and downstream named-externality refusal, \autoref{thm:apophatic-name-boundary-citation-exhaustion} and \autoref{thm:apophatic-name-downstream-named-externality-refusal}. They state that every downstream citation is exhausted by the public refusal rows.

Use socket-gate route exhaustion from \autoref{thm:apophatic-name-socket-gate-route-exhaustion}. A consumer that enters through the socket still passes through the requested supply row, refusal gate, ledger, transport, continuation, provenance, and local naming row.

The non-escape certificate and refusal transport totality, \autoref{thm:apophatic-name-non-escape-certificate} and \autoref{thm:apophatic-name-refusal-transport-totality}, rule out every attempted replacement by a witness, quotient representative, hidden theorem, host object, supplied dependency, assumed proposition, or closure principle. Therefore the only consumable downstream boundary is the finite refusal packet.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_downstream\_boundary\_consumption}

\begin{theorem}[ApophaticName classifier-refusal transport]
\label{thm:apophatic-name-classifier-refusal-transport}
Let $A=(S,R,G,L,H,C,P,N)$ and $A'=(S',R',G',L',H',C',P',N')$ be accepted $\ApophaticNameUp$ packets whose socket, request, refusal-gate, ledger, continuation, package, and naming rows are related by the displayed componentwise $\hsame$ transports. Then the transported classifier carries the refusal ledger of $A$ to the refusal ledger of $A'$ through the displayed $\Cont$, $\Pkg$, and $\NameCert$ rows, and it cannot turn the named externality into an internal object, assumed proposition, quotient representative, hidden theorem, or host-side datum.
\end{theorem}
\begin{proof}
Read both carriers through \autoref{def:apophatic-name-carrier}. The only classifier-facing coordinates are the socket, request, gate, ledger, transport, continuation, provenance, and local name.

Use \autoref{thm:apophatic-name-refusal-classifier-stability}. The componentwise $\hsame$ rows preserve the refusal classifier while moving from $A$ to $A'$.

Now transport the ledger itself. The $\Cont$ routes replay the same consumer read, the $\Pkg$ row preserves provenance, and the local $\NameCert$ row names the transported packet as another accepted ApophaticName carrier.

The non-escape certificate and classifier stability rule out every attempted replacement by generated content. Since neither carrier has a coordinate for an internal object, assumed proposition, quotient representative, hidden theorem, or host-side datum, the transported refusal remains a refusal ledger.
\end{proof}

\begin{theorem}[ApophaticName consumer-boundary exhaustion]
\label{thm:apophatic-name-consumer-boundary-exhaustion}
Every downstream consumer of an accepted $\ApophaticNameUp$ packet factors through the displayed $\BHist$ rows
$$
S,R,G,L,H,C,P,N.
$$
The consumer may read the socket name, requested supply shape, refusal gate, refusal ledger, componentwise $\hsame$ transport, $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$ row, and no further consumer boundary exists for host equality, quotient representatives, hidden theorem content, generated witnesses, or supplied external objects.
\end{theorem}
\begin{proof}
Start with the ledger nonescape theorem \autoref{thm:apophatic-name-ledger-nonescape}. It sends every downstream read through the displayed refusal ledger and excludes hidden proof, host equality, quotient representative, generated witness, and closure-principle routes.

Apply source-refusal totality from \autoref{thm:apophatic-name-source-refusal-totality}. The source side has already been exhausted by the socket, request, gate, ledger, transport, continuation, package, and naming rows.

Apply classifier-refusal transport from \autoref{thm:apophatic-name-classifier-refusal-transport}. Any transported consumer sees the same finite refusal surface through $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rather than a new supplied object.

Thus the consumer boundary is exhausted by $S,R,G,L,H,C,P,N$. There is no remaining carrier coordinate from which host equality, quotient representatives, hidden theorem content, generated witnesses, or supplied external objects could be read.
\end{proof}

\begin{theorem}[ApophaticName gate-source compatibility]
\label{thm:apophatic-name-gate-source-compatibility}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the socket row $S$, requested supply row $R$, refusal gate $G$, and refusal ledger $L$ remain one displayed source surface under the componentwise $\hsame$ row $H$ and the displayed $\Cont$ route row $C$. A downstream consumer may transport and replay this source surface only as $S,R,G,L,H,C,P,N$; it cannot separate the request from the refusal gate or turn the gate into an internal supply.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:apophatic-name-carrier}. The socket, request, gate, and ledger are introduced as four coordinates of the same finite $\BHist$ packet, with $H$ and $C$ recording only componentwise transport and displayed route replay.

Apply \autoref{thm:apophatic-name-source-refusal-totality}. It exhausts the source side by $S,R,G,L,H,C,P,N$ and sends every attempted read of the requested supply through the refusal ledger before any consumer can ask for content.

Finally compare the boundary with the sibling socket and gate surfaces. The socket consumer surface \autoref{thm:apophatic-socket-consumer-surface} keeps the named socket visible, while the gate-question visible-socket nonescape row \autoref{thm:apophatic-gate-question-visible-socket-nonescape} keeps the refusal decision attached to that socket. Thus $\hsame$ and $\Cont$ preserve one displayed source surface rather than splitting off a hidden supply coordinate.
\end{proof}

\begin{theorem}[ApophaticName downstream socket route exactness]
\label{thm:apophatic-name-downstream-socket-route-exactness}
Every downstream read of an accepted $\ApophaticNameUp$ packet factors exactly through
$$
S,R,G,L,H,C,P,N.
$$
The route first reads the socket row and requested supply shape, then the refusal gate and refusal ledger, then the componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ApophaticNameUp}$ row. No downstream consumer has a route to a generated witness, assumed proposition, quotient representative, hidden theorem, host-side datum, or supplied external object outside these rows.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. It states that every downstream consumer is already confined to $S,R,G,L,H,C,P,N$ and that no further consumer boundary exists for host equality, quotient representatives, hidden theorem content, generated witnesses, or supplied external objects.

Use \autoref{thm:apophatic-name-gate-source-compatibility} to keep the first four rows as one source surface. The socket and request rows are readable only together with the refusal gate and refusal ledger, so a consumer cannot bypass $G$ or $L$ while still claiming to read the named dependency.

The sibling socket and gate references give the same exactness at the boundary. The socket noninternalization boundary \autoref{thm:apophatic-socket-noninternalization-boundary} excludes replacement by a generated object, and the visible gate-question boundary \autoref{thm:apophatic-gate-question-visible-socket-nonescape} excludes replacement by an admitted supply. Replaying those rows through $H,C,P,N$ gives precisely the stated downstream route.
\end{proof}

\begin{theorem}[ApophaticName gate-ledger separation]
\label{thm:apophatic-name-gate-ledger-separation}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the socket row $S$, refusal gate $G$, and refusal ledger $L$ remain separate readable rows while being transported together by $H,C,P,N$. The gate records the refusal decision, the ledger records permitted reads and barred conversions, and the socket row remains the visible downstream handle; none of these rows is absorbed into another row or converted into supplied content.
\end{theorem}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_gate\_ledger\_separation}
\begin{proof}
Project $A$ through \autoref{def:apophatic-name-carrier}. The socket, request, gate, and ledger are distinct coordinates of the finite carrier, while $H,C,P,N$ are the displayed transport, replay, provenance, and local naming rows.

Use the sibling surfaces named by the chapter introduction. \autoref{thm:apophatic-socket-consumer-surface} keeps the socket readable as a socket boundary, and \autoref{thm:apophatic-gate-question-visible-socket-nonescape} keeps the gate attached to that visible boundary without admitting the requested supply.

Finally apply \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-downstream-socket-route-exactness}. They transport the separate socket, gate, and ledger rows together through $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, while excluding generated witnesses, host data, quotient representatives, hidden theorems, assumed propositions, and supplied external objects.
\end{proof}

\begin{theorem}[ApophaticName socket-refusal correspondence]
\label{thm:apophatic-name-socket-refusal-correspondence}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
each downstream read of the socket row $S$ corresponds to the refusal recorded by $G$ and ledgered by $L$. The correspondence is transported only through the displayed $\hsame$ row $H$, the $\Cont$ route $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert$ row $N$; it is not a route to the refused external object.
\end{theorem}
\begin{proof}
Begin with downstream socket route exactness. \autoref{thm:apophatic-name-downstream-socket-route-exactness} says that every downstream read factors through $S,R,G,L,H,C,P,N$ and has no route outside those rows.

Compare the socket and gate sides. The socket boundary of \autoref{thm:apophatic-socket-noninternalization-boundary} prevents the visible socket from becoming a generated object, while \autoref{thm:apophatic-gate-question-visible-socket-nonescape} prevents the refusal gate from becoming an admitted supply.

The correspondence is therefore the displayed refusal route itself. Transport through $H$, replay through $C$, provenance through $P$, and naming through $N$ preserve the same socket-refusal packet and do not add host equality, quotient representatives, hidden theorem content, or supplied external content.
\end{proof}

\begin{theorem}[ApophaticName ledger-refusal transport exactness]
\label{thm:apophatic-name-ledger-refusal-transport-exactness}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
transport of the refusal ledger is exact: any transported downstream consumer reads the same refusal relation between $S$, $R$, and $G$ through $L,H,C,P,N$, and no transported route can replace the ledger by a generated witness, host-side datum, quotient representative, hidden theorem, assumed proposition, or supplied external dependency.
\end{theorem}
\begin{proof}
Start from classifier-refusal transport, \autoref{thm:apophatic-name-classifier-refusal-transport}. It moves the refusal classifier componentwise through $H$ and replays the consumer route through $C,P,N$.

Use ledger nonescape and source-refusal totality, \autoref{thm:apophatic-name-ledger-nonescape} and \autoref{thm:apophatic-name-source-refusal-totality}. Together they exhaust every source-side and downstream read by the displayed ledgered packet.

Finally apply gate-ledger separation and socket-refusal correspondence. The first keeps $S,G,L$ as separate finite rows, and the second identifies every socket read with the same refusal route, so the transported ledger remains exact over $S,R,G,L,H,C,P,N$ and exposes no unlisted content.
\end{proof}

\begin{theorem}[ApophaticName closure refusal package]
\label{thm:apophatic-name-closure-refusal-package}
The accepted $\ApophaticNameUp$ carrier assembles a five-row refusal package:
\begin{enumerate}
\item carrier admission for $A=(S,R,G,L,H,C,P,N)$;
\item classifier stability for the socket, request, gate, ledger, transport, route, provenance, and naming rows;
\item ledger exactness for permitted socket reads and barred conversions;
\item non-escape from generated witnesses, assumed propositions, quotient representatives, hidden theorems, host-side data, and supplied external objects;
\item downstream socket route exactness through $S,R,G,L,H,C,P,N$.
\end{enumerate}
This package is the local $\NameCert_{\ApophaticNameUp}$ refusal surface, and it supplies no external dependency as internal BEDC content.
\end{theorem}
\begin{proof}
Carrier admission is the displayed tuple in \autoref{def:apophatic-name-carrier}. Classifier stability is supplied by \autoref{thm:apophatic-name-classifier-stability}, which preserves exactly the socket, request, gate, ledger, transport, continuation, package, and naming rows.

Ledger exactness is \autoref{thm:apophatic-name-refusal-ledger} together with \autoref{thm:apophatic-name-ledger-nonescape}. These rows identify the permitted reads and barred conversions and keep every consumer inside the displayed refusal ledger.

The non-escape certificate \autoref{thm:apophatic-name-non-escape-certificate} rules out the attempted conversions to generated objects, assumed propositions, quotient representatives, hidden theorems, and host-side data. Gate-source compatibility adds that the request and refusal gate remain one source surface under $\hsame$ and $\Cont$.

Finally apply \autoref{thm:apophatic-name-downstream-socket-route-exactness}. It packages the boundary read through $S,R,G,L,H,C,P,N$ and the sibling ApophaticSocket and ApophaticGateQuestion surfaces, so the five listed rows form the local closure refusal package without installing the named externality as internal content.
\end{proof}

\begin{theorem}[ApophaticName kernel scope triad]
\label{thm:apophatic-name-kernel-scope-triad}
For every accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N),
$$
the socket-name row $S$, requested-supply row $R$, and refusal-gate row $G$ are read only through the displayed $\mathsf{BHist}$ packet, the componentwise $\hsame$ transport row, the $\Cont$ replay row, the $\Pkg$ provenance row, and the local $\NameCert_{\ApophaticNameUp}$ row. No kernel read separates those three rows into a supplied object, assumed proposition, quotient representative, hidden theorem, or host-side datum.
\end{theorem}
\begin{proof}
Project the accepted carrier by \autoref{def:apophatic-name-carrier}. The rows $S,R,G$ occur inside the same finite $\mathsf{BHist}$ packet as the ledger, transport, continuation, package, and naming rows.

Use the socket carrier and classifier stability theorems, \autoref{thm:apophatic-name-socket-carrier} and \autoref{thm:apophatic-name-classifier-stability}. They keep socket, request, and refusal rows componentwise under $\hsame$ without adding a generated witness.

Finally apply the refusal ledger and consumer-boundary exhaustion, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. These rows force every kernel read through $L,H,C,P,N$, so the triad remains a displayed refusal surface rather than an internal supply.
\end{proof}

\begin{theorem}[ApophaticName supply-shape refusal exactness]
\label{thm:apophatic-name-supply-shape-refusal-exactness}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, the requested supply shape $R$ is exactly the row refused by the gate $G$ and recorded by the ledger $L$. The packet introduces no generated witness, external object, host realization, quotient representative, hidden theorem, or assumed proposition in place of that refused row.
\end{theorem}
\begin{proof}
Read $R$ and $G$ through the carrier definition. The request row and refusal-gate row are adjacent coordinates of the same displayed packet, and the ledger row $L$ records the permitted reads and barred conversions.

Apply source-refusal totality from \autoref{thm:apophatic-name-source-refusal-totality}. It exhausts the source-refusal surface by $S,R,G,L,H,C,P,N$ and sends any attempted content read through the refusal ledger first.

Then use gate-source compatibility and the closure refusal package, \autoref{thm:apophatic-name-gate-source-compatibility} and \autoref{thm:apophatic-name-closure-refusal-package}. They keep the requested supply shape attached to the refusal gate and exclude every coordinate that would turn the request into supplied content.
\end{proof}

\begin{theorem}[ApophaticName downstream refusal replay]
\label{thm:apophatic-name-downstream-refusal-replay}
Every downstream replay of an accepted $\ApophaticNameUp$ packet factors through the refusal ledger $L$, classifier transport by $H$, the displayed $\Cont$ route $C$, $\Pkg$ provenance $P$, the local $\NameCert$ row $N$, and the consumer-boundary exhaustion of $S,R,G,L,H,C,P,N$. The replay exports only the refusal packet and never a generated witness, external object, host-side datum, quotient representative, hidden theorem, or assumed proposition.
\end{theorem}
\begin{proof}
Begin with the refusal ledger of \autoref{thm:apophatic-name-refusal-ledger}. It names the visible socket, request, refusal gate, ledger, transport, continuation, package, and local naming rows.

Apply classifier-refusal transport from \autoref{thm:apophatic-name-classifier-refusal-transport}. Transport moves the refusal ledger through the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows while preserving the refusal classifier.

Finally use downstream socket route exactness and consumer-boundary exhaustion, \autoref{thm:apophatic-name-downstream-socket-route-exactness} and \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. They exhaust every downstream replay by the same finite refusal packet, leaving no route to supplied or host-side content.
\end{proof}

\begin{theorem}[ApophaticName supply-request consumer factorization]
\label{thm:apophatic-name-supply-request-consumer-factorization}
Every consumer read that asks for the requested supply-shape row of an accepted $\ApophaticNameUp$ packet factors through the displayed socket row $S$, requested supply row $R$, refusal gate $G$, refusal ledger $L$, $\hsame$ transport row $H$, $\Cont$ replay row $C$, $\Pkg$ provenance row $P$, and local $\NameCert$ row $N$. The read cannot skip the refusal ledger to obtain an internal object, axiom, quotient representative, hidden theorem, or host datum.
\end{theorem}
\begin{proof}
Project the carrier $A=(S,R,G,L,H,C,P,N)$ from \autoref{def:apophatic-name-carrier}. The requested supply-shape row is not a free-standing source; it is one displayed coordinate of the same refusal packet as the socket, gate, ledger, transport, route, provenance, and naming rows.

Use source-refusal totality from \autoref{thm:apophatic-name-source-refusal-totality}. It sends every accepted source request through $S,R,G,L,H,C,P,N$ and refuses the conversion from requested shape to supplied object.

Apply downstream refusal replay from \autoref{thm:apophatic-name-downstream-refusal-replay}. Replay preserves the same refusal ledger and route rows for downstream consumers, so a supply-shape read is still a ledgered refusal read.

Finally cite the socket and gate boundaries already binding the chapter, \autoref{thm:apophatic-name-socket-carrier}, \autoref{thm:apophatic-name-gate-source-compatibility}, and \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. These boundaries exclude internal objects, axioms, quotient representatives, hidden theorems, and host data from the accepted packet.
\end{proof}

\begin{theorem}[ApophaticName kernel-scope refusal triad]
\label{thm:apophaticname-kernel-scope-refusal-triad}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, every kernel-scope read of the socket-name row $S$, requested supply row $R$, and refusal-gate row $G$ is confined to the concrete BEDC rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert_{\ApophaticNameUp}$. The triad cannot be read as an abstract source equivalence, host object, quotient representative, hidden theorem, assumed proposition, or supplied external dependency.
\end{theorem}
\begin{proof}
Project $A$ through \autoref{def:apophatic-name-carrier}. The socket, request, gate, ledger, transport, continuation, provenance, and naming coordinates are finite $\BHist$ rows.

Use \autoref{thm:apophatic-name-kernel-scope-triad}. It already confines the socket-name, requested-supply, and refusal-gate rows to the displayed packet and forbids their separation into supplied content.

Finally apply \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-obligation-surface}. The ledger and local $\NameCert$ obligations are concrete BEDC rows, so the kernel-scope triad remains a refusal surface rather than an abstract source equivalence.
\end{proof}

\begin{theorem}[ApophaticName source-refusal transport]
\label{thm:apophaticname-source-refusal-transport}
Let $A=(S,R,G,L,H,C,P,N)$ and $A'=(S',R',G',L',H',C',P',N')$ be accepted $\ApophaticNameUp$ packets whose displayed rows are related by the componentwise $\hsame$ transports recorded in $H$ and $H'$. If a consumer reads $A$ only as a source-refusal packet over $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$, then the transported consumer reads $A'$ only through $S',R',G',L',H',C',P',N'$ and still receives no generated witness, host object, quotient representative, hidden theorem, assumed proposition, or supplied external dependency.
\end{theorem}
\begin{proof}
Start from source-refusal totality, \autoref{thm:apophatic-name-source-refusal-totality}. It exhausts the source side of $A$ by the concrete rows $S,R,G,L,H,C,P,N$.

Transport the displayed rows with \autoref{thm:apophatic-name-classifier-refusal-transport}. The $\hsame$ row moves the refusal classifier componentwise, while $\Cont$, $\Pkg$, and $\NameCert$ replay and rename the same refusal packet.

Apply \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. The transported read has no coordinate for supplied content, so $A'$ remains a source-refusal packet over the concrete BEDC rows rather than an abstract equivalence between sources.
\end{proof}

\begin{theorem}[ApophaticName downstream refusal ledger exhaustion]
\label{thm:apophaticname-downstream-refusal-ledger-exhaustion}
Every downstream consumer of an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$ that cites the named externality must exhaust the displayed refusal ledger $L$ together with the $\BHist$ socket and request rows, the $\hsame$ transport row $H$, the $\Cont$ replay row $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\ApophaticNameUp}$ row $N$. After those rows are exhausted, no downstream route remains to a generated BEDC object, host-side datum, quotient representative, hidden theorem, assumed proposition, or supplied external dependency.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:apophatic-name-downstream-refusal-replay}. It forces downstream replay through the refusal ledger, classifier transport, displayed continuation route, package provenance, local name, and consumer-boundary exhaustion.

Use \autoref{thm:apophatic-name-supply-request-consumer-factorization}. A consumer that asks for the requested supply shape is still routed through $S,R,G,L,H,C,P,N$ and cannot skip $L$.

Finally cite \autoref{thm:apophatic-name-downstream-socket-route-exactness} and \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. Together they identify the downstream route as exactly the displayed ledgered packet and exclude every supplied or host-side object outside the local $\NameCert$ surface.
\end{proof}

\begin{theorem}[ApophaticName socket-request gate factorization]
\label{thm:apophatic-name-socket-request-gate-factorization}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, every public read of the socket row $S$ together with the requested supply-shape row $R$ factors through the refusal gate $G$ and refusal ledger $L$ before it reaches the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The factorization exports a public refusal boundary, not a supplied object, host datum, quotient representative, hidden theorem, assumed proposition, or generated witness.
\end{theorem}
\begin{proof}
Project $A$ through \autoref{def:apophatic-name-carrier}. The socket, request, gate, ledger, transport, continuation, provenance, and local name are one finite packet, so the request row is not available as an independent source of content.

Apply the refusal-ledger and non-escape theorems, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-non-escape-certificate}. They identify the permitted public reads and keep every attempted content read behind the refusal ledger.

Now use socket-refusal and source-refusal totality, \autoref{thm:apophatic-name-socket-refusal} and \autoref{thm:apophatic-name-source-refusal-totality}. These force each socket-request read through $G,L,H,C,P,N$ before a downstream consumer can cite the packet.

The resulting public surface is the displayed refusal boundary. Since no coordinate of $A$ stores a supplied object or host realization, the factorization remains a refusal route through the local $\NameCert$ packet.
\end{proof}

\begin{theorem}[ApophaticName boundary citation exhaustion]
\label{thm:apophatic-name-boundary-citation-exhaustion}
Every downstream citation of the named externality carried by an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$ is exhausted by the public boundary rows
$$
S,R,G,L,H,C,P,N.
$$
The citation must pass through the refusal ledger, socket-refusal route, externality handoff, source-refusal totality, and downstream refusal-ledger exhaustion; no further boundary remains for supplied external content, host-side data, quotient representatives, hidden theorem content, assumed propositions, or generated witnesses.
\end{theorem}
\begin{proof}
Start with the socket-request gate factorization of \autoref{thm:apophatic-name-socket-request-gate-factorization}. It places public socket and request reads behind the same gate and ledger rows.

Use externality handoff from \autoref{thm:apophatic-name-externality-handoff}. The handoff lets downstream chapters cite the named dependency only as the finite refusal packet $A$.

Apply source-refusal totality and downstream refusal-ledger exhaustion, \autoref{thm:apophatic-name-source-refusal-totality} and \autoref{thm:apophaticname-downstream-refusal-ledger-exhaustion}. Together they exhaust both the source side and the downstream side by $S,R,G,L,H,C,P,N$.

Finally cite non-escape through \autoref{thm:apophatic-name-non-escape-certificate}. The packet has no coordinate for supplied external content or host realization, so the public boundary citation is exhausted by the displayed refusal rows.
\end{proof}

\begin{theorem}[ApophaticName refusal provenance transport]
\label{thm:apophatic-name-refusal-provenance-transport}
Let $A=(S,R,G,L,H,C,P,N)$ and $A'=(S',R',G',L',H',C',P',N')$ be accepted $\ApophaticNameUp$ packets related by the displayed componentwise $\hsame$ transports. If a downstream consumer cites $A$ only through its public refusal boundary, then the transported citation of $A'$ is again only through $S',R',G',L',H',C',P',N'$ and carries the same refusal provenance through $\Cont$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Begin with classifier-refusal transport, \autoref{thm:apophatic-name-classifier-refusal-transport}. It moves the refusal classifier along the displayed socket, request, gate, ledger, route, provenance, and naming rows without creating a supplied coordinate.

Use source-refusal transport from \autoref{thm:apophaticname-source-refusal-transport}. A consumer that reads $A$ only as a source-refusal packet is transported to a consumer that reads $A'$ only through the corresponding displayed rows.

Now apply boundary citation exhaustion, \autoref{thm:apophatic-name-boundary-citation-exhaustion}. The downstream citation is already exhausted by the public refusal rows, so transport cannot add host data, quotient representatives, hidden theorem content, assumed propositions, or generated witnesses.

The provenance rows $C',P',N'$ therefore replay, package, and name the same refusal boundary for $A'$. This is refusal provenance transport, not transport of the refused external object.
\end{proof}

\begin{theorem}[ApophaticName refusal export totality]
\label{thm:apophatic-name-refusal-export-totality}
For an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$, the complete public export boundary is the refusal packet on $S,R,G,L,H,C,P,N$. Every exported read of the named externality is classified by the socket row, requested supply-shape row, refusal gate, refusal ledger, componentwise transport, continuation route, package provenance, and local $\NameCert$ row, and by no supplied external object.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:apophatic-name-carrier}. The socket, requested supply-shape, gate, ledger, transport, continuation, provenance, and naming rows are the only displayed coordinates.

Apply the refusal ledger and classifier transport boundaries, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-classifier-refusal-transport}. They classify exported reads by the same ledgered refusal packet under componentwise transport.

Finally use consumer boundary exhaustion and downstream refusal ledger exhaustion, \autoref{thm:apophatic-name-consumer-boundary-exhaustion} and \autoref{thm:apophaticname-downstream-refusal-ledger-exhaustion}. Together they leave no exported route to a supplied external object outside $S,R,G,L,H,C,P,N$.
\end{proof}

\begin{theorem}[ApophaticName downstream named-externality refusal]
\label{thm:apophatic-name-downstream-named-externality-refusal}
Every downstream consumer that cites the named externality of an accepted $\ApophaticNameUp$ packet receives only the displayed refusal packet $S,R,G,L,H,C,P,N$. The citation may replay the socket, request, gate, ledger, transport, continuation, provenance, and local naming rows, but it cannot convert the named externality into supplied content, a host datum, a quotient representative, a hidden theorem, or an assumed proposition.
\end{theorem}
\begin{proof}
Start from downstream refusal ledger exhaustion, \autoref{thm:apophaticname-downstream-refusal-ledger-exhaustion}. It requires every downstream consumer to exhaust the displayed refusal ledger together with the socket, request, transport, continuation, provenance, and local naming rows.

Use refusal export totality from \autoref{thm:apophatic-name-refusal-export-totality}. The public export surface is already the refusal packet on $S,R,G,L,H,C,P,N$.

Apply boundary citation exhaustion, \autoref{thm:apophatic-name-boundary-citation-exhaustion}. A downstream citation of the named externality is therefore a citation of the displayed refusal packet and has no remaining coordinate for supplied or host-side content.
\end{proof}

\begin{theorem}[ApophaticName supply request nonimport]
\label{thm:apophatic-name-supply-request-nonimport}
The requested supply row $R$ of an accepted $\ApophaticNameUp$ packet cannot import a supplied object, axiom, quotient representative, hidden theorem, or host datum. It is read only as a requested supply-shape coordinate inside the refusal packet $S,R,G,L,H,C,P,N$, behind the refusal gate $G$ and refusal ledger $L$.
\end{theorem}
\begin{proof}
Project the packet $A=(S,R,G,L,H,C,P,N)$. The row $R$ is a coordinate of the finite refusal carrier, not a source of supplied content.

Apply supply-request consumer factorization, \autoref{thm:apophatic-name-supply-request-consumer-factorization}. Any consumer read asking for $R$ factors through $S,R,G,L,H,C,P,N$ and cannot skip the refusal ledger.

Now use \autoref{thm:apophatic-name-downstream-named-externality-refusal}. Downstream citation still receives only the displayed refusal packet, so the requested supply row cannot import an object, axiom, quotient representative, hidden theorem, or host datum.
\end{proof}

\begin{theorem}[ApophaticName socket refusal totality]
\label{thm:apophatic-name-socket-refusal-totality}
Every socket-facing consumer read of an accepted $\ApophaticNameUp$ packet $A=(S,R,G,L,H,C,P,N)$ must pass through the displayed refusal ledger, classifier-stability row, supply-request gate, and nonimport row before it can cite the packet. The resulting citation is a finite refusal packet over $S,R,G,L,H,C,P,N$, not a supplied object, host datum, quotient representative, hidden theorem, or assumed proposition.
\end{theorem}
\begin{proof}
Begin with the refusal ledger, \autoref{thm:apophatic-name-refusal-ledger}. It identifies the visible socket, request, refusal-gate, ledger, transport, continuation, provenance, and naming rows as the consumer surface.

Use classifier stability from \autoref{thm:apophatic-name-classifier-stability}. Componentwise $\hsame$ transport preserves that same refusal classifier and does not create another socket-facing coordinate.

Now apply the socket-request gate factorization and supply-request nonimport rows, \autoref{thm:apophatic-name-socket-request-gate-factorization} and \autoref{thm:apophatic-name-supply-request-nonimport}. They force a socket-facing read through $G,L,H,C,P,N$ before the packet can be cited downstream.

The packet has no coordinate for supplied content, host data, quotient representatives, hidden theorems, or assumed propositions. Hence every socket-facing citation is total only as the displayed refusal packet.
\end{proof}

\begin{theorem}[ApophaticName contextual class non-escape]
\label{thm:apophatic-name-contextual-class-nonescape}
The refusal surface of an accepted $\ApophaticNameUp$ packet never supplies a contextual-class object, host selector, or imported ontology outside the displayed rows $S,R,G,L,H,C,P,N$. Any attempted contextual-class read is stopped by the refusal ledger, classifier stability, non-escape certificate, and supply-request nonimport boundary.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:apophatic-name-carrier}. The only rows present are the socket, requested supply shape, refusal gate, refusal ledger, transport, continuation, provenance, and local naming row.

Apply the refusal ledger and classifier stability theorems, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-classifier-stability}. They keep every transported consumer read on the same refusal rows.

Use the non-escape certificate, \autoref{thm:apophatic-name-non-escape-certificate}. It rules out conversion of the named externality into a generated object, assumed proposition, quotient class, concealed theorem, or host-side datum.

Finally cite supply-request nonimport, \autoref{thm:apophatic-name-supply-request-nonimport}. Since the request row remains a requested supply-shape coordinate behind the refusal gate, no contextual-class object, host selector, or imported ontology can be supplied by the packet.
\end{proof}

\begin{theorem}[ApophaticName boundary descent ledger]
\label{thm:apophatic-name-boundary-descent-ledger}
Downstream descent through the apophatic boundary of an accepted $\ApophaticNameUp$ packet is ledger-bounded by the local $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. A consumer may descend only by replaying $S,R,G,L$ through $H,C,P,N$, and it cannot add a supplied external object, host selector, imported ontology, quotient representative, hidden theorem, or assumed proposition.
\end{theorem}
\begin{proof}
Start from the carrier definition and the refusal ledger, \autoref{def:apophatic-name-carrier} and \autoref{thm:apophatic-name-refusal-ledger}. They place the boundary in finite $\BHist$ rows and identify $L$ as the ledger for the permitted socket and request reads.

Use classifier stability, \autoref{thm:apophatic-name-classifier-stability}. The descent rows are transported only componentwise along $H$, so the classifier remains attached to the displayed refusal packet.

Apply the non-escape certificate together with supply-request nonimport, \autoref{thm:apophatic-name-non-escape-certificate} and \autoref{thm:apophatic-name-supply-request-nonimport}. These results keep the requested supply shape behind the gate and rule out every conversion to supplied or host-side content.

Thus any downstream descent is exactly a replay through $\Cont$, packaging through $\Pkg$, and citation by the local $\NameCert$ row. The descent is ledger-bounded by $S,R,G,L,H,C,P,N$ and has no other boundary object to export.
\end{proof}

\begin{theorem}[ApophaticName downstream boundary consumer]
\label{thm:apophatic-name-downstream-boundary-consumer}
Every downstream consumer read of an accepted $\ApophaticNameUp$ packet
$$
A=(S,R,G,L,H,C,P,N)
$$
factors through the displayed socket, requested supply-shape, refusal gate, ledger, componentwise transport, continuation, provenance, and local naming rows. The consumer receives only that refusal-boundary packet and no supplied object, quotient representative, hidden theorem, host datum, or generated witness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:apophatic-name-carrier}. The only rows presented to a downstream consumer are $S,R,G,L,H,C,P,N$.

Apply the refusal ledger, obligation surface, and non-escape certificate, \autoref{thm:apophatic-name-refusal-ledger}, \autoref{thm:apophatic-name-obligation-surface}, and \autoref{thm:apophatic-name-non-escape-certificate}. These rows identify the permitted reads, the local NameCert obligations, and the barred conversions for the same packet.

Finally use the sibling socket and gate surfaces already binding this chapter, \autoref{thm:apophatic-name-socket-request-gate-factorization} and \autoref{thm:apophatic-name-boundary-citation-exhaustion}. They force the downstream citation to remain a public refusal-boundary citation rather than a supplied object or host-side witness.
\end{proof}

\begin{theorem}[ApophaticName refusal gate separation]
\label{thm:apophatic-name-refusal-gate-separation}
The refusal gate $G$ separates socket requests from generated witnesses, quotient representatives, hidden theorems, and host objects for every accepted $\ApophaticNameUp$ packet. A read may name the socket row $S$ and requested supply-shape row $R$ only by passing through $G,L,H,C,P,N$, and it cannot turn the request into substrate content.
\end{theorem}
\begin{proof}
Begin with the refusal ledger of \autoref{thm:apophatic-name-refusal-ledger}. It records each permitted socket and request read together with the barred conversions from request to internal content.

Use the non-escape certificate, \autoref{thm:apophatic-name-non-escape-certificate}. It rules out the attempted repackaging of the named externality as a generated object, assumed proposition, quotient class, hidden theorem, or host-side datum.

The socket-request gate factorization and boundary citation exhaustion, \autoref{thm:apophatic-name-socket-request-gate-factorization} and \autoref{thm:apophatic-name-boundary-citation-exhaustion}, keep the request behind $G$ through $\Cont$, $\Pkg$, and $\NameCert$. Hence the gate separates the public request from every hidden or host-side realization.
\end{proof}

\begin{theorem}[ApophaticName NameCert handoff exhaustion]
\label{thm:apophatic-name-namecert-handoff-exhaustion}
The local $\NameCert_{\ApophaticNameUp}$ handoff through $N$ exhausts all public refusal-boundary exports of an accepted packet $A=(S,R,G,L,H,C,P,N)$. Any public export is a replay of the refusal ledger through $H,C,P,N$, not an export of supplied content, a quotient representative, a hidden theorem, a generated witness, or a host object.
\end{theorem}
\begin{proof}
Start from \autoref{thm:apophatic-name-obligation-surface}. Its carrier, classifier-stability, ledger-exactness, continuation, package, and non-escape rows are the local NameCert obligations for the packet.

Apply the refusal ledger and non-escape certificate, \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-non-escape-certificate}. They identify the public refusal rows and exclude every conversion to supplied or host-side content.

Finally cite downstream named-externality refusal and boundary descent, \autoref{thm:apophatic-name-downstream-named-externality-refusal} and \autoref{thm:apophatic-name-boundary-descent-ledger}. Together they show that a downstream export is exhausted by replay through $H,C,P,N$, so the local NameCert handoff has no remaining hidden route to export.
\end{proof}

\begin{theorem}[ApophaticName boundary socket provenance]
\label{thm:apophatic-name-boundary-socket-provenance}
Every boundary citation of an accepted $\ApophaticNameUp$ packet factors through the socket surface, refusal-gate provenance rows, and local $\NameCert$ row in the displayed packet $S,R,G,L,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier and use \autoref{thm:apophatic-name-socket-carrier}; the socket citation is already a read of the finite surface $S,R,G,L,H,C,P,N$.

Apply \autoref{thm:apophatic-name-socket-request-gate-factorization} and \autoref{thm:apophatic-name-namecert-handoff-exhaustion}. The route reaches the local NameCert row only after the socket, request, refusal gate, ledger, transport, continuation, and provenance rows.
\end{proof}

\begin{theorem}[ApophaticName refusal gate route totality]
\label{thm:apophatic-name-refusal-gate-route-totality}
Every accepted refusal route for $\ApophaticNameUp$ is exhausted by the displayed socket, requested supply shape, refusal gate, ledger, $\Pkg$ provenance, and $\NameCert$ rows, together with the recorded $\hsame$ and $\Cont$ routes.
\end{theorem}
\begin{proof}
Use \autoref{thm:apophatic-name-refusal-ledger} and \autoref{thm:apophatic-name-source-refusal-totality}. They identify the permitted refusal route with $S,R,G,L,H,C,P,N$.

Then apply \autoref{thm:apophatic-name-consumer-boundary-exhaustion}. Since no supplied object or hidden theorem is a coordinate, the displayed rows exhaust the route.
\end{proof}

\begin{theorem}[ApophaticName downstream nonimport]
\label{thm:apophatic-name-downstream-nonimport}
Downstream consumers may cite the named externality of an accepted $\ApophaticNameUp$ packet only through its public boundary, and cannot import the refused supply as an internal BEDC object.
\end{theorem}
\begin{proof}
Apply \autoref{thm:apophatic-name-downstream-named-externality-refusal} and \autoref{thm:apophatic-name-supply-request-nonimport}. A downstream citation receives only the refusal packet and not the requested supply.

The non-escape certificate \autoref{thm:apophatic-name-non-escape-certificate} excludes generated witnesses, host data, quotient representatives, hidden theorems, and assumed propositions from the packet.
\end{proof}

\begin{theorem}[ApophaticName bridge-route scope]
\label{thm:apophatic-name-bridge-route-scope}
The public refusal-boundary packet $S,R,G,L,H,C,P,N$ supplies the paper bridge surface from $\ApophaticNameUp$ to downstream named-externality consumers. The bridge route exports socket naming, requested supply shape, refusal gate, refusal ledger, componentwise transport, continuation replay, package provenance, and local $\NameCert$ rows, while importing no supplied object, generated witness, hidden theorem, quotient representative, host datum, or assumed proposition.
\end{theorem}
\begin{proof}
Begin with the downstream nonimport theorem above. It states that downstream consumers may cite the named externality only through the public boundary and cannot import the refused supply as internal BEDC content.

Use \autoref{thm:apophatic-name-refusal-gate-route-totality} and \autoref{thm:apophatic-name-namecert-handoff-exhaustion}. They identify the exported route with the displayed socket, request, gate, ledger, transport, continuation, provenance, and local naming rows.

Finally apply \autoref{thm:apophatic-name-non-escape-certificate}. Since generated witnesses, hidden theorems, quotient representatives, host data, and assumed propositions are excluded from the packet, the bridge surface is a public refusal-boundary route rather than an imported object.
\end{proof}
\leanchecked{BEDC.Derived.ApophaticNameUp.ApophaticNameCarrier\_bridge\_route\_scope}

\closureat{ApophaticNameUp}{scopedStr}
\closureat{ApophaticNameUp}{publicStr}
\closureat{ApophaticNameUp}{bridgedStr}
\closureat{ApophaticNameUp}{matureStr}

\begin{closurestatus}{\ApophaticNameUp}
  \constructivestory{An $\ApophaticNameUp$ packet is generated from a finite socket-name row, a requested supply-shape row, a refusal-gate row, a refusal ledger, componentwise transport, continuation routes, package provenance, and a local naming certificate.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:apophatic-name-carrier}, \autoref{thm:apophatic-name-boundary-request-image-row}, \autoref{thm:apophatic-name-refusal-readback-row}, \autoref{thm:apophatic-name-componentwise-namecert-transport-row}, \autoref{thm:apophatic-name-classifier-stability}, \autoref{thm:apophatic-name-public-boundary-package}, and \autoref{thm:apophatic-name-refusal-audit-package} bind the mature paper surface as the finite socket and refusal tuple, image row, readback row, componentwise NameCert transport, classifier stability, public boundary package, and refusal audit package for named externality.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not supply the external dependency, prove its existence, internalize it as an axiom or quotient, or close a Lean implementation.}
  \upgradepath{The paper axis is closed at the mature finite socket and refusal surface; machine verification and standard bridge checking remain formal-axis obligations for the same public boundary route.}
\end{closurestatus}
