\begin{theorem}[FiniteTraceEvaluator checkpoint-runtime triad]
\label{thm:finite-trace-evaluator-checkpoint-runtime-triad}
For an accepted $\FiniteTraceEvaluatorUp$ packet, the checkpoint row, runtime
row, and image/readback row form one displayed triad
$$
I,T,A,V,H,C,P,N.
$$
The checkpoint side reads the finite $\BHist$ trace through $T$ and the
accepted-result route through $I \to T \to A$; the runtime side reads the same
route through $\hsame$ transports $H$ and displayed $\Cont$ replay routes $C$;
the package and local naming side is recorded by $\Pkg$ provenance $P$ and the
local $\NameCert_{\FiniteTraceEvaluatorUp}$ row $N$.

No checkpoint-runtime consumer receives a host evaluator, hidden runtime
state, unbounded trace source, second checkpoint source, or unchecked compiler
theorem.
\end{theorem}
\begin{proof}
Begin with checkpoint readiness. The totality and readiness rows of
\autoref{thm:finitetraceevaluator-root-checkpoint-totality} and
\autoref{thm:finitetraceevaluator-root-consumer-readiness} place every root
checkpoint read on $I,T,A,V,H,C,P,N$ before any downstream runtime consumer can
inspect the packet.

Next use runtime totality. By
\autoref{thm:finitetraceevaluator-root-runtime-totality}, the runtime row has
the same finite surface and does not add a host evaluator or an unbounded
runtime coordinate.

Finally attach image readback, result factorization, and terminal route
completion. The image and readback rows of
\autoref{thm:finite-trace-evaluator-root-image-row} and
\autoref{thm:finite-trace-evaluator-root-readback-exactness} identify the
visible rows, while
\autoref{thm:finite-trace-evaluator-checkpoint-result-totality} and
\autoref{thm:finitetrace-evaluator-terminal-route-totality} keep the accepted
result on the same finite route. Thus the checkpoint, runtime, and readback
rows form one triad.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator checkpoint image readback]
\label{thm:finite-trace-evaluator-checkpoint-image-readback}
Every checkpoint image of an accepted $\FiniteTraceEvaluatorUp$ packet reads
back through the finite route
$$
I \to T \to A
$$
for accepted results and through $V,H,C,P,N$ for validation-facing reads. The
readback uses the displayed $\BHist$ trace, componentwise $\hsame$ transport,
displayed $\Cont$ replay, $\Pkg$ provenance, and local
$\NameCert_{\FiniteTraceEvaluatorUp}$ row, and it exposes no host validation,
total truth predicate, total halting classifier, unbounded evaluator, infinite
trace, or second checkpoint source.
\end{theorem}
\begin{proof}
First expose the checkpoint image. Apply
\autoref{thm:finite-trace-evaluator-root-image-row}; it lists exactly
$I,T,A,V,H,C,P,N$ as the image rows visible to accepted reads.

Then read back the accepted-result and validation routes. The exactness result
\autoref{thm:finite-trace-evaluator-root-readback-exactness} sends accepted
results through $I \to T \to A$ and validation-facing reads through
$V,H,C,P,N$.

Finally combine result factorization with terminal route completion.
\autoref{thm:finite-trace-evaluator-root-ledger-factorization} and
\autoref{thm:finitetrace-evaluator-terminal-ledger-exhaustion} show that the
downstream runtime checkpoint consumer receives the same finite packet. Since
the ledger has no host or unbounded coordinate, checkpoint readback cannot
escape the displayed image.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator terminal runtime nonescape]
\label{thm:finite-trace-evaluator-terminal-runtime-nonescape}
The terminal runtime route of an accepted $\FiniteTraceEvaluatorUp$ packet is
confined to the finite checkpoint-runtime packet
$$
I,T,A,V,H,C,P,N.
$$
Its $\BHist$ trace row, $\hsame$ transport rows, $\Cont$ replay rows, $\Pkg$
provenance row, and local $\NameCert_{\FiniteTraceEvaluatorUp}$ row are the
only routes available to terminal runtime consumers. It exports no host
evaluator, hidden runtime state, total truth predicate, total halting
classifier, unbounded evaluator, infinite trace semantics, or alternate
checkpoint route.
\end{theorem}
\begin{proof}
Start from the checkpoint-runtime triad of
\autoref{thm:finite-trace-evaluator-checkpoint-runtime-triad}. It identifies
the checkpoint, runtime, and image/readback rows as one finite packet.

Next apply the terminal route results. The terminal route totality and source
stability rows,
\autoref{thm:finitetrace-evaluator-terminal-route-totality} and
\autoref{thm:finitetrace-evaluator-terminal-source-stability}, keep terminal
runtime reads on $I \to T \to A$ under displayed $\hsame$ and $\Cont$
transport.

Finally use terminal ledger exhaustion together with checkpoint image
readback. By
\autoref{thm:finitetrace-evaluator-terminal-ledger-exhaustion} and
\autoref{thm:finite-trace-evaluator-checkpoint-image-readback}, the terminal
consumer receives only $I,T,A,V,H,C,P,N$. Hence none of the excluded host,
truth, halting, unbounded, infinite-trace, or alternate checkpoint coordinates
can be exported.
\end{proof}
