\begin{theorem}[FiniteTraceEvaluator checkpoint row exposure]
\label{thm:finite-trace-evaluator-checkpoint-row-exposure}
For every accepted $\FiniteTraceEvaluatorUp$ packet, the checkpoint-facing surface exposes exactly the input row $I$, finite trace row $T$, accepted-result row $A$, validation-boundary row $V$, componentwise transport row $H$, route row $C$, provenance row $P$, and local $\NameCert_{\FiniteTraceEvaluatorUp}$ row $N$. The exposure is read from the finite carrier and exports no hidden runtime state.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. Its checkpoint-facing coordinates are the input, trace, accepted-result, validation, transport, route, provenance, and local naming rows.

Apply the root NameCert obligation surface of \autoref{thm:finitetrace-evaluator-root-namecert-obligations}. It identifies those coordinates as the public certificate rows of the accepted evaluator packet.

The checkpoint-runtime triad of \autoref{thm:finite-trace-evaluator-checkpoint-runtime-triad} then reads the checkpoint side through the same finite surface. Since the carrier has no separate runtime coordinate, the checkpoint row exposes only $I,T,A,V,H,C,P,N$.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator runtime route totality]
\label{thm:finite-trace-evaluator-runtime-route-totality}
Every runtime-facing read of an accepted $\FiniteTraceEvaluatorUp$ packet factors through the checkpoint route
$$
I \to T \to A \to V
$$
with the transport, route, provenance, and local naming rows $H,C,P,N$ visible. The route is total for the displayed packet and does not require a host evaluator, unchecked validation predicate, unbounded trace, or alternate accepted-result classifier.
\end{theorem}
\begin{proof}
Begin with checkpoint row exposure from \autoref{thm:finite-trace-evaluator-checkpoint-row-exposure}. It supplies the finite packet $I,T,A,V,H,C,P,N$ as the whole runtime-facing surface.

Next use \autoref{thm:finite-trace-evaluator-checkpoint-runtime-acceptance-lock}. It requires every accepted checkpoint-runtime read to pass through the displayed input, trace, accepted-result, validation, transport, route, provenance, and local naming rows.

Finally apply \autoref{thm:finitetrace-evaluator-checkpoint-replay-totality}. The replay reads $I$ before $T$, $T$ before $A$, and then $V,H,C,P,N$, so the runtime route is total on the displayed finite packet and no host evaluator or alternate classifier is imported.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator checkpoint route nonescape]
\label{thm:finite-trace-evaluator-checkpoint-route-nonescape}
No checkpoint-facing consumer of an accepted $\FiniteTraceEvaluatorUp$ packet can escape the displayed route $I,T,A,V,H,C,P,N$. In particular, the consumer cannot replace the input row, finite trace row, accepted-result row, validation row, transport row, route row, provenance row, or local name by hidden runtime state, a host validation coordinate, an unbounded evaluator output, or an alternate evaluator result.
\end{theorem}
\begin{proof}
Start with runtime route totality from \autoref{thm:finite-trace-evaluator-runtime-route-totality}. It places every runtime-facing read on the finite checkpoint route $I \to T \to A \to V$ with $H,C,P,N$ visible.

Use checkpoint-runtime route determinacy from \autoref{thm:finitetrace-evaluator-checkpoint-runtime-route-determinacy}. Componentwise $\hsame$ and displayed $\Cont$ replay identify the route by the exposed rows, so a second checkpoint route cannot be recovered from the same packet.

Now apply runtime acceptance nonescape from \autoref{thm:finitetrace-evaluator-runtime-acceptance-nonescape}. The accepted runtime row exports no host validator, total truth predicate, total halting classifier, unchecked compiler theorem, hidden runtime state, unbounded evaluator, or infinite trace.

Combining these facts, every checkpoint consumer is confined to the displayed input, trace, accepted-result, validation, transport, route, provenance, and local naming rows, and no alternate evaluator output is available.
\end{proof}
