\begin{theorem}[FiniteTraceEvaluator checkpoint-budget exhaustion]
\label{thm:finite-trace-evaluator-checkpoint-budget-exhaustion}
For an accepted $\FiniteTraceEvaluatorUp$ packet
$E=(I,T,A,V,H,C,P,N)$, every checkpoint-budget read consumed by the
$\ReflectionRuntimeCheckpointUp$ sibling surface is exhausted by the displayed
finite evaluator rows: coded input $I$, finite trace $T$, accepted-result
classifier $A$, validation-boundary row $V$, componentwise $\hsame$ transport
$H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local
$\NameCert_{\FiniteTraceEvaluatorUp}$ row $N$. The checkpoint budget exposes no
host evaluator, hidden runtime acceptance predicate, total truth predicate,
total halting classifier, unbounded evaluator, infinite trace, or second
checkpoint source.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-trace-evaluator-carrier}. Its
public $\BHist$ packet has exactly the rows $I,T,A,V,H,C,P,N$; no further
runtime row is part of the carrier.

Apply the terminal root surface of
\autoref{def:finite-trace-evaluator-terminal-root-surface}. It presents the
same rows to the $\ReflectionRuntimeCheckpointUp$ consumer, with $I,T,A$ as the
accepted-result spine and $V,H,C,P,N$ as the validation-boundary and structural
surface.

Finally use the root checkpoint saturation theorem,
\autoref{thm:finite-trace-evaluator-root-checkpoint-namecert-saturation}. It
exhausts checkpoint-state, result, validation-boundary, transport,
continuation, provenance, and local naming reads at the same finite packet.
Since none of the excluded runtime or truth objects is a displayed row, no
checkpoint-budget read can escape the finite surface.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator reflection-runtime route]
\label{thm:finite-trace-evaluator-reflection-runtime-route}
Every $\ReflectionRuntimeCheckpointUp$ route reading an accepted
$\FiniteTraceEvaluatorUp$ packet factors through
$$
I \to T \to A \to V \to H \to C \to P \to N.
$$
The first three rows form the accepted-result route, while the remaining rows
record validation refusal, componentwise $\hsame$ transport, displayed
$\Cont$ replay, $\Pkg$ provenance, and the local
$\NameCert_{\FiniteTraceEvaluatorUp}$ row. The route does not import a host
runtime evaluator or a hidden runtime acceptance predicate.
\end{theorem}
\begin{proof}
Begin with the checkpoint consumer route,
\autoref{thm:finite-trace-evaluator-checkpoint-consumer-route}. It already
places every runtime checkpoint consumer on the displayed sequence from $I$
through $N$.

Next combine the terminal accepted-result readback with terminal validation
nonescape,
\autoref{thm:finite-trace-evaluator-terminal-accepted-result-readback} and
\autoref{thm:finite-trace-evaluator-terminal-validation-nonescape}. The first
result fixes access to $A$ behind $I \to T$, and the second keeps validation at
the boundary row $V$ rather than at a host runtime predicate.

The structural rows then carry only the same route. Componentwise $\hsame$
transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local
$\NameCert$ row expose the finite packet to the
$\ReflectionRuntimeCheckpointUp$ surface without adding evaluator content.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator downstream-unblock scope]
\label{thm:finite-trace-evaluator-downstream-unblock-scope}
The finite evaluator package supplied to downstream reflection-runtime
chapters is exactly the checkpoint-budget package
$$
I,T,A,V,H,C,P,N.
$$
It licenses downstream use of the displayed finite trace, accepted-result row,
validation-boundary refusal, $\BHist$ packet identity, componentwise $\hsame$
transport, displayed $\Cont$ route, $\Pkg$ provenance, and local $\NameCert$
row. It does not license host evaluator validation, hidden runtime acceptance,
total truth for $\mathrm{CIC}^{*}$ sentences, total halting, unbounded
evaluation, infinite trace semantics, or a second runtime checkpoint route.
\end{theorem}
\begin{proof}
First combine
\autoref{thm:finite-trace-evaluator-checkpoint-budget-exhaustion} with
\autoref{thm:finite-trace-evaluator-reflection-runtime-route}. These two
results identify the available budget rows and the only route by which the
runtime checkpoint sibling can read them.

Use \autoref{thm:finite-trace-evaluator-root-exactness-scope} and
\autoref{thm:finite-trace-evaluator-checkpoint-ledger-cut}. They separate the
accepted-result spine from the validation-boundary and structural rows, and
they remove host validation, truth, halting, unbounded evaluation, infinite
trace semantics, and alternate checkpoint sources from the ledger.

Thus any downstream reflection-runtime chapter citing the evaluator receives a
finite $\BHist$ packet with visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$
rows. The cited package unblocks only finite checkpoint reads over those rows,
so no hidden runtime acceptance predicate or host evaluator is exported.
\end{proof}
