\begin{definition}[FiniteTraceEvaluator terminal route carrier]
\label{def:finite-trace-evaluator-terminal-route-carrier}
A $\FiniteTraceEvaluatorUp$ terminal route carrier is a finite packet
$$
E=(T,Q,R,X,H,C,P,N)
$$
whose rows have the following roles. The row $T$ is the finite $\BHist$ trace
row of the evaluator. The row $Q$ is the checkpoint row that reads the trace
as a checkpoint source. The row $R$ is the runtime row exposed to downstream
runtime consumers. The row $X$ is the image and readback row recording the
accepted-result image and the checkpoint readback boundary. The row $H$
records componentwise $\hsame$ transport between the trace, checkpoint,
runtime, and readback rows. The row $C$ is the displayed $\Cont$ replay route.
The row $P$ is the $\Pkg$ provenance row. The row $N$ is the local
$\NameCert_{\FiniteTraceEvaluatorUp}$ row. The carrier has no coordinate for
host validation, hidden runtime state, unbounded evaluation, an infinite trace,
or an unchecked compiler theorem.
\end{definition}

\begin{theorem}[FiniteTraceEvaluator checkpoint-runtime factorization]
\label{thm:finite-trace-evaluator-checkpoint-runtime-factorization}
For every accepted $\FiniteTraceEvaluatorUp$ terminal route carrier
$E=(T,Q,R,X,H,C,P,N)$, checkpoint-facing and runtime-facing reads factor
through the same finite route
$$
T \to Q \to R.
$$
The factorization is transported componentwise by $H$, replayed by $C$,
packaged by $P$, named by $N$, and read back through $X$. It imports no host
evaluator, no hidden runtime row, and no second checkpoint source.
\end{theorem}
\begin{proof}
First expose the checkpoint side with
\autoref{thm:finitetraceevaluator-root-checkpoint-totality} and
\autoref{thm:finitetraceevaluator-root-checkpoint-admission-totality}. These
statements place checkpoint admission on the finite evaluator rows and force
the checkpoint source to be a displayed $\BHist$ route.

Next expose the runtime side with
\autoref{thm:finitetraceevaluator-root-runtime-totality} and
\autoref{thm:finitetrace-evaluator-root-runtime-admission}. Runtime consumers
read the same finite packet through displayed transport, continuation,
provenance, and local naming rows, not through a host evaluator.

Finally attach the checkpoint-runtime surface of
\autoref{thm:finite-trace-evaluator-checkpoint-row-exposure} and
\autoref{thm:finite-trace-evaluator-runtime-route-totality}. It identifies the
checkpoint row and the runtime row as two views of the same finite route, so
the carrier factors through $T \to Q \to R$ with $X,H,C,P,N$ as readback,
transport, replay, provenance, and naming data.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator terminal route exposure]
\label{thm:finite-trace-evaluator-terminal-route-exposure}
Every terminal consumer of an accepted $\FiniteTraceEvaluatorUp$ route carrier
receives exactly the finite surface
$$
T,Q,R,X,H,C,P,N.
$$
The trace row $T$, checkpoint row $Q$, runtime row $R$, image and readback row
$X$, componentwise $\hsame$ row $H$, $\Cont$ replay row $C$, $\Pkg$
provenance row $P$, and local $\NameCert_{\FiniteTraceEvaluatorUp}$ row $N$
are the whole terminal exposure. The consumer cannot recover host validation,
hidden runtime state, unbounded evaluation, an infinite trace, or an unchecked
compiler theorem from the packet.
\end{theorem}
\begin{proof}
Start from the terminal checkpoint surface,
\autoref{thm:finite-trace-evaluator-terminal-checkpoint-accountability}. It
binds terminal checkpoint reads to the finite trace route and keeps validation,
transport, continuation, provenance, and naming inside the displayed packet.

Use the checkpoint-runtime factorization above. It aligns the checkpoint row
with the runtime row through the same finite carrier and leaves image readback
as the row $X$ rather than as a hidden runtime coordinate.

Now apply root image readback,
\autoref{thm:finite-trace-evaluator-root-image-row} and
\autoref{thm:finite-trace-evaluator-root-readback-exactness}. Accepted reads
and checkpoint readback are confined to the displayed image and readback row,
so the terminal consumer sees precisely $T,Q,R,X,H,C,P,N$.
\end{proof}

\begin{theorem}[FiniteTraceEvaluator NameCert terminal obligation surface]
\label{thm:finite-trace-evaluator-namecert-terminal-obligation-surface}
The local $\NameCert_{\FiniteTraceEvaluatorUp}$ obligation surface of a
terminal route carrier $E=(T,Q,R,X,H,C,P,N)$ is exhausted by the following
finite obligations: trace finiteness for $T$, checkpoint admission for $Q$,
runtime totality for $R$, image and readback exactness for $X$, componentwise
$\hsame$ transport for $H$, displayed $\Cont$ replay for $C$, $\Pkg$
provenance for $P$, and local naming for $N$. No NameCert clause asks for host
validation, total truth, total halting, unbounded evaluation, an infinite
trace, or an unchecked compiler theorem.
\end{theorem}
\begin{proof}
First read the local naming row from
\autoref{thm:finite-trace-evaluator-namecert-obligations}. The carrier rows
are exactly the rows that the local $\NameCert_{\FiniteTraceEvaluatorUp}$
surface can certify.

Next combine root checkpoint readiness, root runtime totality, and root image
readback exactness. Theorems
\autoref{thm:finitetraceevaluator-root-consumer-readiness},
\autoref{thm:finitetraceevaluator-root-runtime-totality}, and
\autoref{thm:finite-trace-evaluator-root-ledger-factorization} provide the
checkpoint, runtime, image, and readback obligations on the same finite
packet.

Finally use terminal route exposure above together with
\autoref{thm:finite-trace-evaluator-checkpoint-route-nonescape}. Since every
terminal consumer is confined to $T,Q,R,X,H,C,P,N$, the local NameCert terminal
surface is exhausted by those displayed obligations and has no remaining host
or unbounded evaluator clause.
\end{proof}
