\section{Boundary-Gated World}
\label{sec:boundary-gated-world}

The first executable protocol is deliberately small.  It is not a claim about
large-scale pixel world modeling.  It is a controlled setting that separates
latent recovery from distinction and gap learning.

\paragraph{World.}
The latent state is two-dimensional.  The continuation rule is an
Ornstein--Uhlenbeck pair:
$$
  z_{t+1}=\rho z_t+\sqrt{1-\rho^2}\eta_t .
$$
The observation is a nonlinear shear $x_t=g(z_t)$.  The operational
distinction is an inside/outside radial boundary:
$$
  d_t = \mathbf 1[\lVert z_t\rVert^2\le r^2].
$$
The gap ledger is a boundary band:
$$
  g_t = \mathbf 1[|\lVert z_t\rVert^2-r^2|\le \varepsilon].
$$
Thus the world has a continuous state, a discrete distinction, and an explicit
gap surface.  The distinction is operational because crossing the boundary
changes the inside/outside claim.  The gap is operational because near-boundary
claims are not certified.

\paragraph{Current artifact.}
The lab script \texttt{run\_bedc\_jepa\_boundary\_world.py}, stored under
\path{papers/bedc-quality-lab/scripts/}, generates a canonical evidence
envelope for this protocol.  The experiment script
\texttt{run\_bedc\_jepa\_experiment.py} then runs the four-system comparison:
latent-only prediction, post-hoc probe, post-hoc BEDC report, and trained
BEDC-JEPA gap readback.

\paragraph{Recorded measurements.}
The four-system experiment records:
$$
\begin{array}{ll}
\texttt{S0\_unlogged\_error\_rate} & 0.091146,\\
\texttt{S1\_unlogged\_error\_rate} & 0.080729,\\
\texttt{S2\_unlogged\_error\_rate} & 0.035156,\\
\texttt{S3\_unlogged\_error\_rate} & 0.013021,\\
\texttt{S2\_gap\_detection\_auc} & 0.845039,\\
\texttt{S3\_gap\_detection\_auc} & 0.898880,\\
\texttt{S2\_bedc\_debt\_score} & 0.056448,\\
\texttt{S3\_bedc\_debt\_score} & 0.037607.
\end{array}
$$

All four systems have the same latent recovery score, $0.926199$, in this
controlled setting.  The trained BEDC-JEPA system therefore does not win by
hiding a worse latent model behind a better report.  It keeps the post-hoc
probe's outside-gap distinction accuracy while improving gap AUROC, unlogged
error, and the scope-relative debt score against the post-hoc BEDC report
baseline.

\paragraph{Gradient-trained objective.}
The torch objective artifact trains a latent encoder and predictor, freezes
the recovered latent carrier, and then compares a latent-only distinction
probe with a BEDC objective that trains distinction and gap heads with an
unlogged-error penalty.  The protocol deliberately keeps latent recovery fixed:
both systems have linear identifiability $R^2=0.991837$, covariance deviation
$0.079721$, and orthogonality error $0.033816$.  Under that fixed carrier, the
BEDC objective improves gap AUROC from $0.500000$ to $0.999223$, lowers
unlogged error from $0.007812$ to $0.000000$, and lowers debt from $0.104297$
to $0.007459$.  This is the first gradient-trained BEDC-JEPA objective
artifact in the lab; it is still boundary-world scale, not a public JEPA
implementation comparison.

\paragraph{Seed sweep.}
The experiment also runs a two-world seed sweep: the radial boundary world and
a sinusoidal boundary world.  Across $16$ world-seed cells, the aggregate
trained-minus-post-hoc gap AUROC gain is $0.021994 \pm 0.013291$, the
post-hoc-minus-trained unlogged-error reduction is $0.022868 \pm 0.006128$,
and the post-hoc-minus-trained debt reduction is $0.011947 \pm 0.005406$.
The trained system beats the post-hoc baseline in $81.25\%$ of cells for gap
AUROC, $100\%$ for unlogged error, and $81.25\%$ for debt.

\paragraph{Grid-pixel learned transition.}
A second benchmark uses $11\times 11$ pixel observations of a moving point in a
grid world.  A latent readout is trained from pixels, and a linear
action-conditioned transition model is trained on the learned state.  The
one-step transition score is $R^2=0.998237$ with mean L2 error $0.021983$.
Against the post-hoc grid report baseline, trained BEDC-JEPA improves gap
AUROC from $0.892642$ to $0.999210$, lowers unlogged error from $0.010000$ to
$0.001111$, and lowers debt from $0.029559$ to $0.009579$.
The same learned transition model is used in a three-target planning sweep,
where gap-aware planning improves risk-adjusted cost while exposing a
short-horizon success tradeoff.

\paragraph{MiniGrid-style visual planning.}
A third visual-planning benchmark uses a MiniGrid-style one-hot image
observation with walls, a two-room door passage, a goal region, and a hazard
band.  A state readout is learned from the image observation, and an
action-conditioned transition table is estimated from data.  The learned
one-step transition accuracy is $1.000000$.  Against the post-hoc visual
report baseline, trained BEDC-JEPA improves gap AUROC from $0.571541$ to
$1.000000$ and lowers debt from $0.085692$ to $0.016167$.  Unlogged error is
$0.000000$ for both systems because the goal-cell distinction is directly
readable in this one-hot visual setting.  In a three-target, thirty-six
trajectory planning sweep, gap-aware planning lowers high-gap state rate by
$0.202778$, lowers unsafe-state rate by $0.072222$, and improves
risk-adjusted planning cost by $0.313494$, while reducing raw success rate by
$0.305556$.  This benchmark is still local, but it has the form of a public
partial-observability grid-control task rather than a scalar latent boundary
only.

\paragraph{Object-level counterfactual intervention.}
A fourth benchmark uses two object slots rendered as pixels.  The query is
whether object $A$, after an action intervention, will contact object $B$.
This supplies a Causal-JEPA-style object-level counterfactual readback rather
than a scalar boundary only.  The trained object BEDC-JEPA system reaches
counterfactual accuracy $0.946000$ with intervention sensitivity $0.628799$.
Against the post-hoc object report baseline, it improves outside-gap
distinction accuracy from $0.728553$ to $0.994878$, improves gap AUROC from
$0.518800$ to $0.988137$, lowers unlogged error from $0.263000$ to $0.002000$,
and lowers debt from $0.287323$ to $0.016736$.  Masking object $B$ drops the
trained counterfactual accuracy by $0.373000$, showing that the readback uses
the object slot rather than only action priors.

Across an eight-seed object-intervention sweep, the trained system beats the
post-hoc report in every seed for outside-gap accuracy, gap AUROC, unlogged
error, and debt.  The mean counterfactual accuracy is $0.932750 \pm 0.012035$,
the mean intervention sensitivity is $0.619477 \pm 0.010757$, and the mean
object-slot masking drop is $0.383875 \pm 0.018455$.  The mean gains over the
post-hoc report are $0.267294 \pm 0.016073$ for outside-gap accuracy,
$0.429153 \pm 0.011258$ for gap AUROC, $0.279500 \pm 0.018394$ for unlogged
error reduction, and $0.262087 \pm 0.013921$ for debt reduction.

\paragraph{Multi-object distractor readback.}
A fifth benchmark uses four object slots.  The operational query remains a
counterfactual contact claim about the target pair $(A,B)$ after an
intervention on $A$, while two additional object slots act as distractors.
The gap ledger marks target-pair boundary cases, target-pair occlusion, and
distractor intrusion into the target-pair ambiguity zone.  The trained
multi-object BEDC-JEPA system reaches counterfactual accuracy $0.929167$ and
distractor invariance $0.992408$.  Against the post-hoc multi-object report,
it improves outside-gap distinction accuracy from $0.686111$ to $0.987500$,
improves gap AUROC from $0.511644$ to $0.985894$, lowers unlogged error from
$0.278333$ to $0.000000$, and lowers debt from $0.289213$ to $0.024655$.
Masking the target object slot drops accuracy by $0.365000$, while masking
the distractor slots drops accuracy by only $0.002500$.  This records that the
readback is tied to the declared target distinction rather than to generic
slot presence.

Across a six-seed multi-object sweep, the trained system beats the post-hoc
report in every seed for outside-gap accuracy, gap AUROC, unlogged error, and
debt.  The mean counterfactual accuracy is $0.940972 \pm 0.004162$, and the
mean distractor invariance is $0.992877 \pm 0.000202$.  The mean gains over
the post-hoc report are $0.310598 \pm 0.013975$ for outside-gap accuracy,
$0.497110 \pm 0.013092$ for gap AUROC, $0.277917 \pm 0.010163$ for unlogged
error reduction, and $0.273032 \pm 0.008693$ for debt reduction.  The mean
target-minus-distractor masking gap is $0.381528 \pm 0.009849$.

The same construction is also run with six object slots: one target pair and
four distractors.  Across a four-seed cluttered-object sweep, the trained
system again beats the post-hoc report in every seed for outside-gap accuracy,
gap AUROC, unlogged error, and debt.  The mean counterfactual accuracy is
$0.946607 \pm 0.004367$, and the mean distractor invariance is
$0.992700 \pm 0.000427$.  The mean gains over the post-hoc report are
$0.317471 \pm 0.015747$ for outside-gap accuracy,
$0.501613 \pm 0.017510$ for gap AUROC, $0.270000 \pm 0.004001$ for unlogged
error reduction, and $0.260725 \pm 0.005137$ for debt reduction.  The mean
target-minus-distractor masking gap is $0.382321 \pm 0.016490$.
