\section{Evidence Packet}
\label{sec:evidence-packet}

The local evidence is stored outside this paper as a lab artifact.  The paper
records only the current contact and its boundary.

\paragraph{Artifact pointers.}
The current protocol writes machine-readable artifacts under the quality-lab
reports directory.  The four-system experiment writes:
$$
\begin{array}{ll}
\text{JSON} & \texttt{bedc\_jepa\_four\_system\_experiment.json},\\
\text{Torch objective} & \texttt{bedc\_jepa\_torch\_objective.json},\\
\text{Manifest} & \texttt{bedc\_jepa\_artifact\_manifest.json},\\
\text{Public MiniGrid probe} & \texttt{bedc\_jepa\_public\_minigrid\_probe.json},\\
\text{Public MiniGrid transition} & \texttt{bedc\_jepa\_public\_minigrid\_transition\_packet.json},\\
\text{Public MiniGrid benchmark} & \texttt{bedc\_jepa\_public\_minigrid\_benchmark\_packet.json},\\
\text{Public JEPA registry} & \texttt{bedc\_jepa\_public\_baseline\_registry.json},\\
\text{Public JEPA comparison} & \texttt{bedc\_jepa\_public\_baseline\_comparison.json},\\
\text{Readiness gate} & \texttt{bedc\_jepa\_readiness.json}.
\end{array}
$$
The JSON artifacts are lab-local evidence boundaries.  They are not Python
definitions of BEDC NameCert, closurestatus, origin, or Lean verification
status.

\paragraph{Source specification.}
The source is \texttt{boundary-gated-ou-world}.  Its latent dimension is $2$,
with sample count $768$, $\rho=0.84$, radius $1.0$, and gap width $0.14$.
The nonlinear observation is \texttt{sinusoidal-parabolic-shear}.

\paragraph{Pattern specification.}
The pattern is \texttt{latent-plus-distinction-plus-gap}.  It asks for three
readbacks from the same world process: continuous state recovery, operational
inside-boundary distinction, and boundary gap detection.

\paragraph{Ledger gaps.}
The current boundary envelope records three gaps:
$$
\begin{array}{l}
\texttt{one-boundary-family},\\
\texttt{no-gap-aware-planning-rollout-yet}.
\end{array}
$$
The torch objective artifact supplies gradient-trained BEDC heads for the
boundary readback setting under a frozen-latent protocol: the latent encoder
has the same recovery score in the latent-only and BEDC-objective systems,
while the trained distinction and gap heads lower debt and remove unlogged
error.  The three-seed gradient sweep records mean gap AUROC gain
$0.498762 \pm 0.000467$, mean unlogged-error reduction
$0.009983 \pm 0.002251$, and mean debt reduction
$0.102887 \pm 0.007293$, with no measured change in latent $R^2$.  The
four-system experiment closes part of the boundary-family gap by comparing
BEDC-JEPA readback against post-hoc baselines on radial and sinusoidal
boundary families.  It also adds a grid-pixel benchmark with a learned
action-conditioned transition model, a MiniGrid-style visual planning
benchmark, and an eight-seed two-object counterfactual contact benchmark.  The
object evidence also includes a four-slot distractor benchmark where the
declared target pair must remain separate from two non-target object slots,
with a six-seed sweep for the distractor setting.  The same target-pair
readback is also evaluated in a six-slot cluttered-object sweep with four
distractors.  The remaining gaps are broader.  The planning rollouts are still
local and synthetic rather than robot-control scale.

\paragraph{Debt items.}
The current debt items are scale debt, public-baseline debt, dependency debt,
and artifact debt.  Scale debt means the learned-transition and
object-intervention benchmarks are small.  Public-baseline debt means the
comparison is local and not yet run against a public JEPA implementation.
Dependency debt means the public MiniGrid packets have executable DoorKey
contracts but record unavailable status in the current environment because
\texttt{gymnasium} and \texttt{minigrid} are absent.  The transition packet
samples Gymnasium image observations and discrete actions when the
dependencies are present.  The benchmark packet computes a public DoorKey
readback/gap metric contract with distinction accuracy, gap AUROC, unlogged
error, certified coverage, and scope-relative debt.  Artifact debt means the
current package is a research branch rather than a cleaned external review
bundle.

\paragraph{External-contact readiness.}
The readiness gate records \texttt{not\_contact\_ready}.  The local torch
objective seed sweep, local visual planning benchmark, and cluttered
object-counterfactual benchmark pass their evidence gates.  The blocking gates
are public MiniGrid execution and public JEPA baseline comparison.  This paper
therefore treats the current packet as an internal research branch, not yet as
an external-contact bundle.
