\section{BEDC-JEPA Model Principle}
\label{sec:model-principle}

\begin{definition}[BEDC-JEPA state]
A BEDC-JEPA state is a triple
$$
  s_t = (z_t,d_t,g_t),
$$
where $z_t \in \mathbb R^m$ is a continuous latent state, $d_t \in [0,1]^K$
is a family of operational distinction scores, and $g_t \in [0,1]^R$ is a
family of gap-ledger scores.  A distinction score is admissible only when its
meaning is tied to a transition, intervention, or planning consequence.  A
gap score marks a boundary, uncertainty, or unsupported claim surface.
\end{definition}

A standard JEPA-style model trains an encoder and predictor to align future
representations:
$$
  \mathcal L_z =
  \lVert P_\omega(E_\theta(o_t),a_t)-\operatorname{sg}(E_\theta(o_{t+1}))\rVert^2.
$$
BEDC-JEPA keeps this representation-space target, but the learning problem is
not exhausted by it.  The model also learns which distinctions can be stably
carried by the state, and which cases must be treated as gaps.

\paragraph{Training objective.}
The target objective has the form
$$
\begin{aligned}
\mathcal L_{\mathrm{BEDC\mbox{-}JEPA}}
={}&\mathcal L_z
+\lambda_d\mathcal L_d
+\lambda_s\mathcal L_{\mathrm{stab}}
+\lambda_i\mathcal L_{\mathrm{intervention}}\\
&+\lambda_g\mathcal L_{\mathrm{gap}}
+\lambda_u\mathcal L_{\mathrm{unlogged}}
+\lambda_p\mathcal L_{\mathrm{plan}} .
\end{aligned}
$$
The distinctive term is $\mathcal L_{\mathrm{unlogged}}$: when a model is
wrong on a declared critical distinction, a relevant gap output must activate.
The model may be wrong inside its declared scope, but it must not be silently
and confidently wrong.

\begin{proposition}[Post-hoc reports are not model objectives]
If two systems have the same model class, same data, same optimizer, and same
training objective, and the second system only writes a NameCert or ledger
report after training, then the second system is not a new learning objective.
\end{proposition}

\begin{proof}
The parameter update rule and objective landscape are unchanged.  The learned
representation is generated by the same optimization problem.  A report can
change evaluation, auditability, or governance, but it does not change the
set of optima or the training dynamics.
\end{proof}

\begin{proposition}[BEDC-JEPA changes the learning problem]
If a nonconstant BEDC regularizer depends on distinction heads, gap heads,
intervention consistency, or unlogged errors, and its coefficient is positive,
then the resulting objective is a different learning problem from the latent
prediction objective alone.
\end{proposition}

\begin{proof}
Let
$$
  \mathcal L'=\mathcal L_z+\lambda R_{\mathrm{BEDC}}
$$
with $\lambda>0$ and $R_{\mathrm{BEDC}}$ nonconstant over the model class.
There exist parameter settings on which $R_{\mathrm{BEDC}}$ differs.  Hence
the objective values and, in general, the minimizing set differ from those of
$\mathcal L_z$ alone.
\end{proof}
