\begin{theorem}[Transported stationary window-seal tail cofinality totality]
\label{thm:transported-stationary-window-seal-tail-cofinality-totality}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet. Every accepted read of the tail schedule attached to $T$ passes first through the $\TailCofinalityScheduleUp$ packet on the displayed $\StreamNameUp$ row $S$ and $\RegSeqRatUp$ row $G$, together with the support rows $H,C,P,N$, before it reaches any finite envelope row $W$ or $\RealUp$ seal row $E$.

Consequently the tail-facing obligation surface of $T$ is the finite route
$$
\begin{aligned}
  R,S,G,H,C,P,N
  \longrightarrow
  \TailCofinalityScheduleUp
  \longrightarrow
  W
  \longrightarrow
  E,
\end{aligned}
$$
with no earlier envelope, detached tail oracle, quotient stream, host equality, selected limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with \autoref{thm:transported-stationary-window-seal-root-regseqrat-window-ownership}. It assigns the $\RegSeqRatUp$ seal $G$ to the constant $\StreamNameUp$ window $S$ already carried by the accepted packet.

Next use \autoref{thm:transported-stationary-window-seal-tail-schedule-envelope-order}. The tail schedule row is read before the finite envelope and before the Real-facing seal, so a tail-facing consumer has no route that reaches $W$ or $E$ first.

Finally apply \autoref{thm:transported-stationary-window-seal-real-regseqrat-source-totality} and \autoref{thm:transported-stationary-window-seal-namecert-route-exhaustion}. These identify the Real source and the public NameCert surface with the displayed rows only, hence the tail schedule read is total over the stated finite route.
\end{proof}

\begin{theorem}[Transported stationary window-seal dyadic radius readback]
\label{thm:transported-stationary-window-seal-dyadic-radius-readback}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet. The dyadic-radius evidence consumed by $T$ is exactly the $\DyadicRatCoreUp$ readback attached to the constant $\StreamNameUp$ window $S$ and the $\RegSeqRatUp$ seal $G$. It is not a separate radius oracle and it does not add a coordinate beyond the displayed $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\FiniteWindowEnvelopeUp$, $\RealUp$, $\BHist/\hsame/\Cont/\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
First apply \autoref{thm:transported-stationary-window-seal-root-regseqrat-window-ownership}. The window and regular-sequence rows are owned by the same transported source triad, so the radius readback is tied to $S$ and $G$ rather than to an independent oracle.

Then use \autoref{thm:transported-stationary-window-seal-tail-schedule-envelope-order}. The dyadic evidence is consumed on the same route that places the tail schedule before the finite envelope and Real seal.

The non-escape side is supplied by \autoref{thm:transported-stationary-window-seal-root-real-seal-nonescape} and \autoref{thm:transported-stationary-window-seal-namecert-route-exhaustion}. Since the Real seal and NameCert route expose only the displayed packet rows, a second dyadic-radius source has no public coordinate on the accepted surface.
\end{proof}

\begin{theorem}[Transported stationary window-seal Real handoff non-escape]
\label{thm:transported-stationary-window-seal-real-handoff-nonescape}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet. Every $\RealUp$ or Completion handoff through $T$ factors through the displayed route
$$
\begin{aligned}
  R,S,G
  \longrightarrow
  \TailCofinalityScheduleUp
  \longrightarrow
  W
  \longrightarrow
  E
  \longrightarrow
  H,C,P,N .
\end{aligned}
$$
The handoff exports no quotient stream, host equality, selected limit, choice coordinate, detached radius oracle, or real-completeness coordinate.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:transported-stationary-window-seal-real-regseqrat-source-totality}. It states that the Real-facing row $E$ is sourced only through the transported $\RatUp$, $\StreamNameUp$, and $\RegSeqRatUp$ triad together with the displayed support rows.

Next apply \autoref{thm:transported-stationary-window-seal-tail-schedule-envelope-order}. It inserts the tail cofinality schedule and finite envelope in the only order compatible with the transported triad and the Real-facing seal.

Finally use \autoref{thm:transported-stationary-window-seal-root-real-seal-nonescape} and \autoref{thm:transported-stationary-window-seal-namecert-route-exhaustion}. These exclude quotient streams, host equality, selected limits, choice, detached radius data, and real-completeness witnesses from the exported route, so the Real or Completion handoff remains inside $R,S,G,W,E,H,C,P,N$.
\end{proof}
