\begin{definition}[Transported stationary window-seal source-triad completion packet]
\label{def:transported-stationary-window-seal-source-triad-completion-packet}
For an accepted $\TransportedStationaryWindowSealUp$ packet $T=(R,S,G,W,E,H,C,P,N)$, the source-triad completion packet is the finite BEDC route consisting of:
\begin{enumerate}
  \item the transported source triad $R,S,G$, where $R$ is the transported $\RatUp$ source row, $S$ is the constant $\StreamNameUp$ window row, and $G$ is the $\RegSeqRatUp$ seal row owned by that window;
  \item the finite envelope and seal rows $W,E$, where $W$ is the $\FiniteWindowEnvelopeUp$ row read after the triad and $E$ is the $\RealUp$-facing seal row read after $W$;
  \item the support rows $H,C,P,N$, carrying the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data for the same route;
  \item the completion-facing consumer route
  $$
  \begin{aligned}
    R,S,G,H,C,P,N
    \longrightarrow
    W
    \longrightarrow
    E
    \longrightarrow
    \CompletionUp .
  \end{aligned}
  $$
\end{enumerate}
The packet has no coordinate for quotient streams, host equality, selected host limits, choice, ambient real completeness, or hidden tail oracles; every such consumer must read the same displayed source triad before it can use the envelope row or the Real-facing seal.
\end{definition}

\begin{theorem}[Transported stationary window-seal source-window admission]
\label{thm:transported-stationary-window-seal-source-window-admission}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet equipped with its source-triad completion packet. The packet admits a source-window triad only in the displayed form $R,S,G$: $R$ is the transported $\RatUp$ classifier row, $S$ is the constant $\StreamNameUp$ finite-window row, and $G$ is the $\RegSeqRatUp$ seal row owned by that window. No accepted read of $T$ can replace this triad by a detached classifier, a moving stream window, or an independent seal source.
\end{theorem}
\begin{proof}
Read the accepted carrier through the NameCert obligation surface of \autoref{thm:transported-stationary-window-seal-namecert-obligations}. Its coordinates are exactly $R,S,G,W,E,H,C,P,N$, and the source side is exposed before the envelope and Real-facing rows.

The seed-window readback fixes the finite-window coordinate. By \autoref{thm:transported-stationary-window-seal-root-regseqrat-window-ownership}, the $\RegSeqRatUp$ seal $G$ is owned by the same constant $\StreamNameUp$ row $S$, while $R$ supplies the transported $\RatUp$ classifier for that row.

Ledger non-escape then excludes alternate admissions. The package and naming rows $P,N$, together with the displayed $\BHist$, $\hsame$, and $\Cont$ support in $H,C$, leave no coordinate from which a detached classifier, moving window, or independent $\RegSeqRatUp$ source could be read.
\end{proof}

\begin{theorem}[Transported stationary window-seal stationary transport coherence]
\label{thm:transported-stationary-window-seal-stationary-transport-coherence}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet equipped with its source-triad completion packet. The stationary handoff row $H$ and route table $C$ preserve the same $R \to S \to G$ route componentwise under $\hsame$ and $\Cont$. Hence transport through $H,C$ cannot create a detached $\RegSeqRatUp$ source or a second stream-name route for the seal.
\end{theorem}
\begin{proof}
Readback determinacy first fixes the order of the source side. The route table can be consumed only after the accepted packet has exposed $R,S,G$, and \autoref{thm:transported-stationary-window-seal-root-envelope-readback-totality} keeps every later envelope read downstream from that source route.

The root window-ownership clause controls the seal coordinate. By \autoref{thm:transported-stationary-window-seal-root-regseqrat-window-ownership}, the row $G$ is a $\RegSeqRatUp$ seal on the same constant $\StreamNameUp$ row $S$, so componentwise $\hsame$ may identify transported presentations of that row but cannot allocate a new source for $G$.

Finally, the Real-seal route forces coherence through completion-facing use. Apply \autoref{thm:transported-stationary-window-seal-real-factorization} and \autoref{thm:transported-stationary-window-seal-root-real-seal-nonescape}: the $\Cont$ data in $C$ carries the displayed source route into $W$ and $E$, and no detached $\RegSeqRatUp$ row is available outside that route.
\end{proof}

\begin{theorem}[Transported stationary window-seal completion handoff nonescape]
\label{thm:transported-stationary-window-seal-completion-handoff-nonescape}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet equipped with its source-triad completion packet. Every completion-facing consumer of $T$ must pass through the displayed rows $R,S,G,W,E,H,C,P,N$. In particular, such a consumer cannot import quotient streams, host equality, choice, selected limits, or ambient real-completeness data in place of the transported $\RatUp$ classifier, constant $\StreamNameUp$ finite window, $\RegSeqRatUp$ seal, finite envelope, Real-facing seal, and support rows.
\end{theorem}
\begin{proof}
The downstream handoff package is rooted in the displayed packet. Use \autoref{thm:transported-stationary-window-seal-l10-handoff-obligation-basis} and \autoref{thm:transported-stationary-window-seal-downstream-route-readiness}: they expose the completion-facing route only through the source triad, finite envelope, Real-facing seal, and the rows $H,C,P,N$.

The Real seal supplies no external escape. By \autoref{thm:transported-stationary-window-seal-root-real-seal-nonescape} and \autoref{thm:transported-stationary-window-seal-real-regseqrat-source-totality}, the row $E$ is read from the finite $\RegSeqRatUp$ route through $W$, not from host equality, selected limits, choice, or real-completeness assumptions.

NameCert route exhaustion handles the remaining consumers. Apply \autoref{thm:transported-stationary-window-seal-namecert-route-exhaustion}: the local name and package rows $N,P$, together with $\BHist$, $\hsame$, and $\Cont$ in $H,C$, enumerate the accepted handoff coordinates, so any completion-facing consumer that preserves $T$ has no off-route coordinate for quotient streams or independent completion data.
\end{proof}

\begin{theorem}[Transported stationary window-seal envelope RealUp totality]
\label{thm:transported-stationary-window-seal-envelope-realup-totality}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet equipped with its source-triad completion packet. Every $\RealUp$-facing read of $E$ and every completion-facing read that preserves $E$ factors through the $\StreamNameUp/\RegSeqRatUp$ source triad and the $\FiniteWindowEnvelopeUp$ row before the Real seal. More precisely, the read route is determined by
$$
\begin{aligned}
  R,S,G
  \longrightarrow
  W
  \longrightarrow
  E ,
\end{aligned}
$$
together with the displayed support rows $H,C,P,N$.
\end{theorem}
\begin{proof}
First use the carrier and NameCert obligation surface of \autoref{thm:transported-stationary-window-seal-namecert-obligations}. It exposes the accepted packet only through $R,S,G,W,E,H,C,P,N$, with componentwise transport, package provenance, and local naming.

Next apply \autoref{thm:transported-stationary-window-seal-root-regseqrat-window-ownership}. This fixes the $\RegSeqRatUp$ row $G$ as a seal on the same finite $\StreamNameUp$ row $S$, so the route cannot reach a finite envelope before the source triad has been read.

Finally use \autoref{thm:transported-stationary-window-seal-real-factorization}, \autoref{thm:transported-stationary-window-seal-root-envelope-exhaustion}, and the L10 handoff basis of \autoref{thm:transported-stationary-window-seal-l10-handoff-obligation-basis}. These place the finite envelope row $W$ between the source triad and the Real-facing row $E$, and they keep completion consumers on that same finite route.
\end{proof}

\begin{theorem}[Transported stationary window-seal completion route nonescape]
\label{thm:transported-stationary-window-seal-completion-route-nonescape}
Let $T=(R,S,G,W,E,H,C,P,N)$ be an accepted $\TransportedStationaryWindowSealUp$ packet equipped with its source-triad completion packet. No completion-facing consumer preserving $T$ can import quotient streams, host equality, selected limits, choice, ambient real completeness, or a hidden tail oracle. Such a consumer has access only to the transported source triad, the finite envelope, the Real seal row, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support rows.
\end{theorem}
\begin{proof}
Begin with readback determinacy, using \autoref{thm:transported-stationary-window-seal-root-envelope-readback-totality}. It orders every accepted completion-facing read through the transported rows before the finite envelope and the Real seal can be consumed.

The Real side is controlled by \autoref{thm:transported-stationary-window-seal-root-real-seal-nonescape} and \autoref{thm:transported-stationary-window-seal-real-regseqrat-source-totality}. These rule out host equality, selected limits, choice, and ambient real completeness as sources for the seal row, because $E$ is sourced by the displayed $\RegSeqRatUp$ route and the finite envelope.

It remains to exclude off-route completion data. Apply \autoref{thm:transported-stationary-window-seal-completion-consumer-boundary}, \autoref{thm:transported-stationary-window-seal-tail-cofinality-handoff}, and \autoref{thm:transported-stationary-window-seal-real-regseq-consumer-exactness}. The sibling L10 handoff files force any tail or completion consumer back through the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\FiniteWindowEnvelopeUp$, and $\RealUp$ route, leaving no coordinate for a hidden tail oracle or independent completion source.
\end{proof}
