\begin{definition}[Bool public endpoint constructors]
\label{def:bool-public-endpoint-constructors}
The public false constructor is $\mathsf{BoolEndpoint}(\bzero)=\emp$, and the
public true constructor is $\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$. Public boolean
operations are finite endpoint tables whose input and output rows are drawn
only from these two constructor rows. No row in this public surface is a host
proposition, a decidable predicate, or an eliminator.
\end{definition}

\begin{theorem}[Bool public constructor case readback]
\label{thm:bool-public-constructor-case-readback}
Every public Bool endpoint read is classified by exactly one of the displayed false
and true endpoint rows of \autoref{def:bool-public-endpoint-constructors}. Two
public constructor readbacks agree exactly when their underlying marks are
related by $\msame$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bool-history-carrier-endpoint-coverage} to the public read.
It supplies a displayed mark $v:\mathsf{BMark}$ and a witness that the read
history is the endpoint $\mathsf{BoolEndpoint}(v)$.

Case analysis on $v$ gives the two public rows
$\mathsf{BoolEndpoint}(\bzero)=\emp$ and $\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$.
Theorem~\ref{thm:bool-endpoint-readback-determinism}
gives uniqueness of the readback mark, and
\autoref{thm:bool-endpoint-bridge-exactness} identifies agreement of endpoint
rows with $\msame$ of the underlying marks.
\end{proof}

\begin{theorem}[Bool public surface no-hidden leakage]
\label{thm:bool-public-surface-no-hidden-leakage}
A consumer of the public Bool surface can read only the two constructor endpoint rows,
endpoint-table operation rows over those constructors, the mark and history
classifier rows, and the semantic certificate ledger. It cannot read a host
proposition, a decidable predicate, an eliminator, or truth-table completeness.
\end{theorem}
\begin{proof}
The public constructors are exactly the two endpoint rows in
\autoref{def:bool-public-endpoint-constructors}. The endpoint coverage and
constructor case readback statements show that public reads return one of these rows,
with agreement controlled by $\msame$ and endpoint exactness rather than by host logic.

The semantic certificate in \autoref{thm:bool-concrete-semantic-namecert}
records the carrier, classifier, and ledger discipline. Since the displayed
public rows contain no host proposition, decidable predicate, eliminator, or
truth-table-completeness row, those objects are not available to a surface
consumer.
\end{proof}

The endpoint coverage, endpoint bridge classifier completeness, and endpoint
readback theorems justify the Bool public-object readback and bridge promised
by the roadmap template; they are not internal fields of the
$\mathsf{SemanticNameCert}$ constructor.
\OptionUp consumes this two-row endpoint discipline as its absent/present tag
surface in \autoref{ch:concrete-instances-option-namecert}.

\begin{corollary}[$\BoolUp$ certificate scope]
\label{cor:bool-certificate-scope}
Theorem~\ref{thm:concrete-bool-namecert} cites the checked core history
$\NameCert$ for $\mathsf{BoolHistoryCarrier}$ and
$\mathsf{BoolHistoryClassifier}$, namely the $BEDC.Derived.BoolUp$ Lean target
$\mathsf{bool\_history\_name\_certificate}$. The public-object
$\mathsf{SemanticNameCert}$ scope is checked separately at
Theorem~\ref{thm:bool-concrete-semantic-namecert} by the $BEDC.Derived.BoolUp$
Lean target $\mathsf{bool\_history\_semantic\_name\_certificate}$. Thus the core
certificate, the mark-level ledger definition, the generic carrier-as-ledger
implication, and the closed semantic certificate occupy separate roles. In each
case $\BoolUp$ is derived from mark and history sameness, and is not primitive.
\end{corollary}

\begin{lemma}[Bool public endpoint forgetful projection boundary]
\label{lem:bool-public-endpoint-forgetful-projection-boundary}
The public constructor surface of \autoref{def:bool-public-endpoint-constructors} admits a BEDC-native forgetful projection. Start with a public constructor readback row and erase the constructor-row name, endpoint-table name, and public-surface annotation while retaining the displayed endpoint history. The retained target data are exactly
$$
\mathsf{BoolHistoryCarrier},\quad
\mathsf{BoolHistoryClassifier},\quad
\mathsf{BoolHistoryCarrier}\text{ as source, pattern, and ledger},\quad
\NameCert(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}),
$$
together with the public semantic certificate
$$
\mathsf{SemanticNameCert}(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryCarrier},
\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}).
$$
More concretely, each retained public read has a mark $v:\BMark$ and an endpoint witness $\hsame(h,\mathsf{BoolEndpoint}(v))$, unique up to $\msame$. For two retained reads $h,k$ with endpoint witnesses through $v,w:\BMark$, the projected classifier row $\mathsf{BoolHistoryClassifier}(h,k)$ holds exactly when $\msame(v,w)$ holds. The projection retains no constructor-row name, endpoint-table name, host proposition, decidable predicate, eliminator, truth-table-completeness datum, payload carrier, payload classifier, or option-packaging row.
\end{lemma}
\begin{proof}
The public constructor rows are exactly the two endpoint rows displayed in \autoref{def:bool-public-endpoint-constructors}. Applying \autoref{thm:bool-public-constructor-case-readback} to a public read supplies a mark $v:\BMark$ and an endpoint witness $\hsame(h,\mathsf{BoolEndpoint}(v))$, and \autoref{thm:bool-endpoint-readback-determinism} makes the displayed mark unique up to $\msame$.

The retained carrier coordinate is forced by \autoref{thm:bool-history-carrier-endpoint-coverage}: an endpoint witness against $\mathsf{BoolEndpoint}(v)$ repacks as $\mathsf{BoolHistoryCarrier}(h)$, and every Bool carrier row is covered by such an endpoint witness. Thus erasing the public constructor name leaves a history in the same target carrier rather than a separate codomain carrier.

For the classifier coordinate, take two retained reads $h,k$ with endpoint witnesses through $v,w$. If $\msame(v,w)$ holds, the reverse direction of \autoref{thm:bool-history-classifier-mark-readback-exactness} rebuilds $\mathsf{BoolHistoryClassifier}(h,k)$ from the two endpoint witnesses and the mark comparison. Conversely, if $\mathsf{BoolHistoryClassifier}(h,k)$ holds, \autoref{thm:bool-history-classifier-mark-readback-exactness} supplies endpoint witnesses through marks $v',w'$ with $\msame(v',w')$. The readback determinism theorem compares $v$ with $v'$ and $w$ with $w'$, and transitivity of mark sameness gives $\msame(v,w)$. Hence the classifier retained by the projection is exactly the mark-level agreement already visible in the constructor readback.

The certificate coordinates are fixed by \autoref{def:bool-history-semantic-fields}, \autoref{thm:concrete-bool-namecert}, and \autoref{thm:bool-concrete-semantic-namecert}. Source, pattern, and ledger are all the same predicate $\mathsf{BoolHistoryCarrier}$, the core name certificate is $\NameCert(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier})$, and the public semantic certificate is the displayed carrier-self semantic certificate. Finally, \autoref{thm:bool-public-surface-no-hidden-leakage} excludes host propositions, decidable predicates, eliminators, and truth-table completeness, while the Bool public surface contains no payload carrier, payload classifier, or option-packaging coordinate. Those named rows are therefore erased rather than transported by the forgetful projection.
\end{proof}

\begin{lemma}[Bool public endpoint constructor classifier alignment boundary]
\label{lem:bool-public-endpoint-constructor-classifier-alignment-boundary}
For histories $h,k:\BHist$, the public Bool endpoint surface aligns its classifier boundary exactly with the two displayed constructor endpoint rows:
$$
\begin{aligned}
&\mathsf{BoolHistoryClassifier}(h,k) \\
&\quad\Longleftrightarrow\quad
  \exists v,w:\BMark,\ e_v,e_w:\BHist,\
    \mathsf{BoolSourceSpec}(v)
    \land
    \mathsf{BoolSourceSpec}(w)
    \land
    \bigl((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp))\bigr)
    \land
    \bigl((w=\bzero \land e_w=\emp) \lor (w=\bone \land e_w=\Eone(\emp))\bigr)
    \land
    \hsame(h,e_v)
    \land
    \hsame(k,e_w)
    \land
    \msame(v,w).
\end{aligned}
$$
Under this equivalence, the transported public rows are exactly the two endpoint readback rows against the endpoint histories $e_v$ and $e_w$ determined by $\mathsf{BoolEndpoint}(v)$ and $\mathsf{BoolEndpoint}(w)$, together with the mark-comparison row $\msame(v,w)$. The retained certificate rows are the carrier, classifier, and semantic ledger rows named by the Bool semantic certificate. Rows for host propositions, decidable predicates, eliminators, and truth-table completeness are forgotten by the public endpoint classifier boundary.
\end{lemma}
\begin{proof}
The displayed equivalence is \autoref{thm:bool-source-qualified-classifier-readback-exactness} read through the explicit endpoint-history witnesses supplied by \autoref{def:bool-public-endpoint-constructors}. Its forward direction says that a classifier comparison between $h$ and $k$ exposes only source-qualified marks $v,w$, endpoint histories $e_v,e_w$ with the displayed constructor equations, the two endpoint readback rows
$\hsame(h,e_v)$ and
$\hsame(k,e_w)$, and the mark-comparison row $\msame(v,w)$. Its reverse direction says that precisely those rows rebuild the Bool history classifier comparison, so no further classifier coordinate is being transported.

By \autoref{def:bool-public-endpoint-constructors}, the public constructors are only
$\mathsf{BoolEndpoint}(\bzero)=\emp$ and
$\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$. The case readback theorem \autoref{thm:bool-public-constructor-case-readback} therefore identifies every public endpoint read with exactly one of those two rows, and \autoref{thm:bool-endpoint-readback-determinism} makes the chosen mark unique up to $\msame$. The endpoint bridge exactness of \autoref{thm:bool-endpoint-bridge-exactness} then makes the row comparison a mark comparison rather than a host-logical comparison.

The certificate side contributes no extra public row. The semantic certificate in \autoref{thm:bool-concrete-semantic-namecert} records the Bool carrier, classifier, and ledger discipline over the same history carrier. Finally, \autoref{thm:bool-public-surface-no-hidden-leakage} states that the public surface does not expose a host proposition, decidable predicate, eliminator, or truth-table completeness row. Hence the boundary transports exactly the two constructor readback rows and their $\msame$ classifier comparison, retains only the semantic certificate ledger rows, and forgets the non-public rows listed above.
\end{proof}

\begin{lemma}[Bool public constructor target-source mirror boundary]
\label{lem:bool-public-constructor-target-source-mirror-boundary}
For the public Bool constructor surface of \autoref{def:bool-public-endpoint-constructors}, the target-facing constructor read and the source-facing carrier read are the same finite endpoint packet viewed in opposite directions. Concretely, a public target read through either displayed constructor row
$\mathsf{BoolEndpoint}(\bzero)=\emp$ or
$\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$ has a source mirror consisting exactly of the same mark $v:\BMark$, an endpoint history witness $e_v:\BHist$ satisfying
$((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp)))$, the same readback observation row $\hsame(h,e_v)$, the same classifier comparison row $\msame(v,w)$ when another constructor read is compared through a mark $w:\BMark$ and endpoint history witness $e_w:\BHist$ satisfying
$((w=\bzero \land e_w=\emp) \lor (w=\bone \land e_w=\Eone(\emp)))$, and the same semantic certificate rows
$$
\mathsf{BoolHistoryCarrier},\quad
\mathsf{BoolHistoryClassifier},\quad
\NameCert(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}),\quad
\mathsf{SemanticNameCert}(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryCarrier},
\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}).
$$
Thus the source side is obtained by renaming the displayed target endpoint packet back to its carrier readback packet. The boundary is negative for any larger mirror: there is no separate source-side constructor carrier, result row, termination row, host proposition row, decidable predicate row, eliminator row, truth-table-completeness row, payload carrier row, payload classifier row, or option-packaging row.
\end{lemma}
\begin{proof}
Start with a public target read. By \autoref{def:bool-public-endpoint-constructors}, the only target constructor rows are
$\mathsf{BoolEndpoint}(\bzero)=\emp$ and
$\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$. The case readback theorem \autoref{thm:bool-public-constructor-case-readback} therefore supplies a displayed mark $v:\BMark$ and an endpoint history witness $e_v:\BHist$ with
$((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp)))$, and identifies the read with the endpoint readback row $\hsame(h,e_v)$. Its agreement clause, together with \autoref{thm:bool-endpoint-readback-determinism} and \autoref{thm:bool-endpoint-bridge-exactness}, says that any comparison between two such reads is exactly the mark comparison $\msame(v,w)$.

The source mirror is forced by endpoint coverage. The reverse direction of \autoref{thm:bool-history-carrier-endpoint-coverage} repacks the readback row $\hsame(h,e_v)$, for an endpoint witness $e_v$ satisfying
$((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp)))$, as the source carrier row $\mathsf{BoolHistoryCarrier}(h)$, while the forward direction says that every source carrier row used by this Bool surface is covered by such an endpoint readback. Hence the target row and source row do not form two independent constructors; they are the same displayed history endpoint read as target endpoint or as source carrier.

For compared reads $h,k$, \autoref{thm:bool-history-classifier-mark-readback-exactness} identifies the source-side classifier row $\mathsf{BoolHistoryClassifier}(h,k)$ with the two endpoint readbacks through marks $v,w$, endpoint history witnesses $e_v,e_w:\BHist$ satisfying
$((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp)))$ and
$((w=\bzero \land e_w=\emp) \lor (w=\bone \land e_w=\Eone(\emp)))$, and the same comparison row $\msame(v,w)$. The source-qualified form in \autoref{thm:bool-source-qualified-classifier-readback-exactness} adds only the already displayed source qualification of those two finite marks, so it does not introduce a further target or source coordinate.

The certificate rows are exactly the rows already named by \autoref{def:bool-history-semantic-fields}, \autoref{thm:concrete-bool-namecert}, and \autoref{thm:bool-concrete-semantic-namecert}: source, pattern, and ledger are all read as $\mathsf{BoolHistoryCarrier}$, and the classifier is $\mathsf{BoolHistoryClassifier}$. Finally, \autoref{thm:bool-public-surface-no-hidden-leakage}, \autoref{lem:bool-public-endpoint-forgetful-projection-boundary}, and \autoref{lem:bool-public-endpoint-constructor-classifier-alignment-boundary} rule out the larger mirror coordinates listed in the statement. The target-source mirror therefore closes exactly at the finite endpoint packet and its Bool semantic certificate rows.
\end{proof}

\begin{lemma}[Bool public endpoint bridge cut-elimination boundary]
\label{lem:bool-public-endpoint-bridge-cut-elimination-boundary}
The public Bool endpoint constructors of \autoref{def:bool-public-endpoint-constructors} admit a bridge cut-elimination boundary over the displayed local rows. For a final consumer read of the public Bool surface, every route row factors through the finite packet
$$
\begin{gathered}
\mathsf{BoolEndpoint}(\bzero)=\emp,\quad
\mathsf{BoolEndpoint}(\bone)=\Eone(\emp),\\
v,w:\BMark,\quad e_v,e_w:\BHist,\\
\bigl((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp))\bigr),\\
\bigl((w=\bzero \land e_w=\emp) \lor (w=\bone \land e_w=\Eone(\emp))\bigr),\\
\hsame(h,e_v),\quad
\hsame(k,e_w),\quad
\msame(v,w),\\
\mathsf{BoolHistoryCarrier},\quad
\mathsf{BoolHistoryClassifier},\quad
\NameCert(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}),\\
\mathsf{SemanticNameCert}(\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryCarrier},
\mathsf{BoolHistoryCarrier},\mathsf{BoolHistoryClassifier}).
\end{gathered}
$$
The two displayed constructor endpoint rows, the endpoint history readback rows, the mark-comparison row, and the carrier, classifier, core certificate, and semantic certificate rows are noneliminable at this boundary: removing any one of them loses either the public endpoint choice, the readback into a history, the classifier comparison, or the certificate surface consumed by the final Bool object. Every other named coordinate appearing in the local public-surface discussion is eliminated or rejected: constructor-row names, endpoint-table names, and public-surface annotations are projected away; host propositions, decidable predicates, eliminators, truth-table-completeness data, payload carriers, payload classifiers, option-packaging rows, separate source-side constructor carriers, result rows, termination rows, and continuation rows are not consumer-visible rows of this Bool endpoint bridge.
\end{lemma}
\begin{proof}
The finite endpoint rows are exactly the two rows displayed in \autoref{def:bool-public-endpoint-constructors}. Thus any public constructor read begins at either
$\mathsf{BoolEndpoint}(\bzero)=\emp$ or
$\mathsf{BoolEndpoint}(\bone)=\Eone(\emp)$, and no third constructor, host predicate, or eliminator row is available at the source of the route. Applying \autoref{thm:bool-public-constructor-case-readback} to the read supplies a mark $v:\BMark$ and an endpoint history witness $e_v:\BHist$ with
$((v=\bzero \land e_v=\emp) \lor (v=\bone \land e_v=\Eone(\emp)))$ and $\hsame(h,e_v)$; applying it to a second read supplies $w:\BMark$ and an endpoint history witness $e_w:\BHist$ with
$((w=\bzero \land e_w=\emp) \lor (w=\bone \land e_w=\Eone(\emp)))$ and $\hsame(k,e_w)$. The uniqueness part is controlled by \autoref{thm:bool-endpoint-readback-determinism}, so the chosen endpoint mark cannot be replaced by an unlisted host or source coordinate.

The comparison row is also forced. By \autoref{thm:bool-endpoint-bridge-exactness}, comparison of the two endpoint rows is exactly comparison of their marks by $\msame(v,w)$. Equivalently, \autoref{thm:bool-history-classifier-mark-readback-exactness} identifies the history classifier row $\mathsf{BoolHistoryClassifier}(h,k)$ with the two endpoint history readbacks and the same mark-comparison row. Hence a bridge consumer cannot keep an independent comparison route after those readback rows have been exposed; the classifier route has already cut through the endpoint packet.

The carrier and certificate side is fixed by the already displayed projection boundary. By \autoref{thm:bool-history-carrier-endpoint-coverage}, the endpoint readback through $e_v$ repacks as the carrier row $\mathsf{BoolHistoryCarrier}(h)$, and every carrier row used here is covered by such an endpoint readback. By \autoref{lem:bool-public-endpoint-forgetful-projection-boundary}, erasing constructor-row names, endpoint-table names, and public-surface annotations leaves exactly the carrier, classifier, carrier-as-source-pattern-ledger, core $\NameCert$, and public semantic certificate rows. By \autoref{def:bool-history-semantic-fields}, \autoref{thm:concrete-bool-namecert}, and \autoref{thm:bool-concrete-semantic-namecert}, these rows are the Bool history carrier, the Bool history classifier, and the carrier-self semantic certificate displayed in the statement.

The remaining possible cuts are negative. \autoref{thm:bool-public-surface-no-hidden-leakage} excludes host propositions, decidable predicates, eliminators, and truth-table completeness from the public consumer surface. \autoref{lem:bool-public-endpoint-constructor-classifier-alignment-boundary} shows that the classifier boundary transports only the two endpoint readback rows and their $\msame$ comparison, while \autoref{lem:bool-public-constructor-target-source-mirror-boundary} shows that target-facing and source-facing reads are the same finite endpoint packet rather than separate constructor carriers, result rows, termination rows, or continuation rows. Since the local chapter displays no additional host, source, handoff, continuation, payload, or option-packaging coordinate, any such coordinate is rejected as unlisted rather than retained by the bridge.

Consequently the final consumer-visible surface is precisely the finite packet named in the statement. The endpoint rows, readback rows, mark-comparison row, carrier and classifier rows, and the two certificate rows are noneliminable because they are the rows used to reconstruct the endpoint choice, the history read, the classifier comparison, and the public Bool certificate. All other local route names are either projected away by the forgetful boundary or excluded by the public-surface and mirror-boundary theorems.
\end{proof}
