\chapter{A Concrete Naming Certificate for \(\OptionUp\)}
\label{ch:concrete-instances-option-namecert}

The optional value interface \(\OptionUp\) is licensed over any source carrier already endowed with a \(\NameCert\). The carrier is the inductive sum of an absent constructor and a present constructor wrapping a witness of the source. It is not a primitive type former; it is licensed only via its underlying inductive carrier and the classifier that lifts the source classifier through the present constructor.

\section{Roadmap template status}

\begin{enumerate}
  \item \textbf{Traditional target}: optional data with one absent value and present values over a source object.
  \item \textbf{BEDC source}: any licensed source carrier $A$ equipped with its existing name certificate.
  \item \textbf{Carrier choice}: the typed $\mathsf{OptionCarrier}$ has $\mathsf{none}$ and $\mathsf{some}$ constructors, while the checked history carrier is the nullable envelope $\mathsf{OptionHistoryCarrier}_S(h)\equiv \hsame(h,\emp)\lor S(h)$.
  \item \textbf{Classifier choice}: the typed $\mathsf{OptionClassifierSpec}$ relates only matching option tags through the source classifier; $\mathsf{OptionHistoryClassifier}$ is the nullable-history classifier consisting of endpoint envelope-carrier witnesses and endpoint $\hsame$.
  \item \textbf{Stability obligations}: typed optional carrier transport, typed absent/present separation, lifted typed classifier symmetry and transitivity, nullable-history endpoint transport, nullable-history classifier symmetry and transitivity, and for the constructor-tagged optional-history certificate a payload coherence condition converting source-carrier $\hsame$ between middle payloads into the source classifier.
  \item \textbf{Ledger}: the typed option interface records the absent-or-present tag and present payload evidence, while the checked nullable-history envelope ledger records only the raw envelope-carrier witness and the raw-to-visible $\hsame$ link.
  \item \textbf{Core theorem list}: typed carrier cases, typed absent/present no-confusion, present inversion, typed classifier equivalence, tagged present-present exactness, tagged mixed-tag separation, nullable-history carrier transport, nullable-history classifier transport, and the nullable-history semantic certificate.
  \item \textbf{Exactness predicate}: matching-tag exactness belongs to $\mathsf{OptionClassifierSpec}$; the tagged history classifier has present-present exactness through visible $e1$ endpoints and mixed-tag separation, while the checked nullable-history classifier exactness is endpoint envelope membership plus endpoint $\hsame$ and carries no present constructor tag.
  \item \textbf{Standard bridge}: the absent branch reads as $\mathsf{none}$ and the present branch reads as $\mathsf{some}(a)$.
  \item \textbf{Status}: the nullable history-envelope $\mathsf{SemanticNameCert}$ is $\mathsf{CheckedCert}$; the constructor-tagged optional-history certificate is $\mathsf{ProofTarget}$.
\end{enumerate}

\section{Carrier definition}

\begin{definition}[Option carrier]
\label{def:option-carrier}
For a licensed source carrier \(A\), define an inductive carrier with constructors \(\mathsf{none}\) and \(\mathsf{some}(a)\).
\end{definition}
\leanchecked{BEDC.Derived.OptionUp.OptionCarrier\_cases}

The checked BEDC-history carrier used below is the nullable semantic carrier $\mathsf{OptionHistoryCarrier}_S(h)\equiv \hsame(h,\emp)\lor S(h)$, not a tagged history carrier.

\section{The certificate}

\begin{definition}[Option source specification]
\label{def:option-source-specification}
The source is the source NameCert for \(A\), lifted through the optional carrier.
\end{definition}
\leandef{BEDC.Derived.OptionUp.OptionHistoryCarrier}

\begin{theorem}[Option history carrier transport]
\label{thm:option-history-carrier-hsame-transport}
If two BEDC histories are internally the same, then optional history-carrier
membership transfers from the first history to the second.
\end{theorem}
\begin{proof}
Invert the optional carrier witness. In the absent branch, compose the
symmetric history-sameness link with the stored empty-history witness. In the
source branch, eliminate the $\hsame(h,k)$ witness, so $k$ is definitionally
the same history as $h$, and reuse the source witness.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryCarrier\_hsame\_transport}

\begin{definition}[Option pattern specification]
\label{def:option-pattern-specification}
The pattern is absent-or-present generation: one null constructor and one wrapper constructor over source witnesses.
\end{definition}

\begin{definition}[Option classifier specification]
\label{def:option-classifier-specification}
The typed classifier relates \(\mathsf{none}\) only to \(\mathsf{none}\), and relates \(\mathsf{some}(a)\) to \(\mathsf{some}(a')\) exactly when the source classifier relates \(a\) and \(a'\). The checked history-level classifier for $\mathsf{OptionHistoryCarrier}$ is the nullable classifier: both endpoints lie in the empty-or-source envelope, and the endpoints are related by $\hsame$.
\end{definition}
\leandef{BEDC.Derived.OptionUp.OptionClassifierSpec}
\leanchecked{BEDC.Derived.OptionUp.optionClassifierSpec\_cases}
\leandef{BEDC.Derived.OptionUp.OptionClassifier}
\leandef{BEDC.Derived.OptionUp.OptionHistoryClassifier}
\leanchecked{BEDC.Derived.OptionUp.OptionClassifierSpec\_none\_some\_absurd}
\leanchecked{BEDC.Derived.OptionUp.optionClassifier\_some\_iff}
\leanchecked{BEDC.Derived.OptionUp.option\_classifier\_inversion}

\begin{definition}[Tagged option history carrier]
\label{def:tagged-option-history-carrier}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, define $\mathsf{TaggedOptionHistoryCarrier}_S(h)$ by the two constructor-shaped cases:
\begin{enumerate}
  \item absent: $\hsame(h,\emp)$;
  \item present: there is a payload history $a$ such that $S(a)$ and $\hsame(h,\Eone(a))$.
\end{enumerate}
\end{definition}

\begin{theorem}[Tagged option history present inversion]
\label{thm:tagged-option-history-present-inversion}
For any BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$ and
history $h$, a present endpoint in the tagged carrier exposes a source payload:
$$
\mathsf{TaggedOptionHistoryCarrier}_S(\Eone(h))
\quad\Longrightarrow\quad
\exists a:\mathsf{BHist}.\; S(a)\land \hsame(h,a).
$$
\end{theorem}
\begin{proof}
Case-analyze the tagged carrier witness for $\Eone(h)$. The absent branch gives
$\hsame(\Eone(h),\emp)$ and is eliminated by generated-history no-confusion
between a present endpoint and the empty endpoint. The present branch gives a
payload history $a$, a source witness $S(a)$, and
$\hsame(\Eone(h),\Eone(a))$; applying the one-constructor inversion theorem for
$\hsame$ strips the visible present tags and yields $\hsame(h,a)$, so $a$ is the
required payload.
\end{proof}

\begin{definition}[Tagged option history classifier]
\label{def:tagged-option-history-classifier}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$ and source classifier $\sim_S$, define $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)$ by the two constructor-matching cases:
\begin{enumerate}
  \item absent-absent: $\hsame(h,\emp)$ and $\hsame(k,\emp)$;
  \item present-present: there are payload histories $a,b$ such that $S(a)$, $S(b)$, $a\sim_S b$, $\hsame(h,\Eone(a))$, and $\hsame(k,\Eone(b))$.
\end{enumerate}
\end{definition}

\begin{theorem}[Tagged option history mixed endpoint separation]
\label{thm:tagged-option-history-mixed-endpoint-separation}
For every BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$,
source classifier $\sim_S$, and payload history $h$, the tagged option history
classifier cannot relate the absent endpoint to the visible present endpoint in
either order:
$$
\neg\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,\Eone(h))
\quad\text{and}\quad
\neg\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\emp).
$$
\end{theorem}
\begin{proof}
Case-analyze the tagged classifier witness. For
$\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,\Eone(h))$, the
absent-absent branch contains $\hsame(\Eone(h),\emp)$, contradicting
one-versus-empty no-confusion. The present-present branch contains
$\hsame(\emp,\Eone(a))$ for some source payload $a$, contradicting
empty-versus-one no-confusion. The opposite mixed endpoint
$\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\emp)$ is identical
with the two endpoint contradictions exchanged: absent-absent gives
$\hsame(\Eone(h),\emp)$, while present-present gives $\hsame(\emp,\Eone(b))$
for the target payload $b$.
\end{proof}

\begin{theorem}[Tagged option history present-present exactness]
\label{thm:tagged-option-history-present-present-exactness}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, source classifier $\sim_S$, and histories $h,k$, the tagged option history classifier is exact on two visible present endpoints:
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\Eone(k))
\quad\Longleftrightarrow\quad
\exists a,b:\mathsf{BHist}.\; S(a)\land S(b)\land \hsame(h,a)\land \hsame(k,b)\land a\sim_S b.
$$
\end{theorem}
\begin{proof}
For the forward direction, case-analyze the tagged classifier witness. The absent-absent branch would contain $\hsame(\Eone(h),\emp)$ and is eliminated by one-versus-empty no-confusion. The present-present branch gives payload histories $a,b$, source witnesses $S(a)$ and $S(b)$, a source classifier witness $a\sim_S b$, and endpoint witnesses $\hsame(\Eone(h),\Eone(a))$ and $\hsame(\Eone(k),\Eone(b))$; one-constructor inversion strips the visible $e1$ tags and yields $\hsame(h,a)$ and $\hsame(k,b)$. For the reverse direction, the displayed payload data rebuilds the present-present classifier branch after applying one-constructor congruence for $\hsame$ to the two payload endpoint witnesses.
\end{proof}

\begin{definition}[Tagged option source hsame compatibility]
\label{def:tagged-option-source-hsame-compatibility}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$ and source classifier $\sim_S$, define $\mathsf{TaggedOptionSourceHsameCompatible}(S,\sim_S)$ to be the property that for all payload histories $a,b$, if $S(a)$, $S(b)$, and $\hsame(a,b)$, then $a\sim_S b$.
\end{definition}

\begin{theorem}[Tagged option hsame source compatibility]
\label{thm:tagged-option-source-hsame-compatibility-hsame}
For every BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$,
$$
\mathsf{TaggedOptionSourceHsameCompatible}(S,\hsame)
$$
holds.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:tagged-option-source-hsame-compatibility}. Given payload histories $a,b$, source witnesses $S(a)$ and $S(b)$, and the displayed witness $\hsame(a,b)$, return that same history-sameness witness as the source classifier witness.
\end{proof}

\begin{definition}[Tagged option history pattern]
\label{def:tagged-option-history-pattern}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, the visible tag pattern $\mathsf{TaggedOptionHistoryPattern}_S(h)$ holds exactly when $h$ is either an absent endpoint with $\hsame(h,\emp)$ or a present endpoint with payload history $a$ satisfying $S(a)$ and $\hsame(h,\Eone(a))$.
\end{definition}

\begin{definition}[Tagged option history ledger]
\label{def:tagged-option-history-ledger}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, the visible tag ledger $\mathsf{TaggedOptionHistoryLedger}_S(h)$ records the same two endpoint forms as certificate data: the absent record stores $\hsame(h,\emp)$, and the present record stores a payload history $a$ together with $S(a)$ and $\hsame(h,\Eone(a))$.
\end{definition}

\begin{theorem}[Tagged option history carrier, pattern, and ledger equivalence]
\label{thm:tagged-option-history-carrier-pattern-ledger-equivalence}
For every BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$ and history $h$, the tagged option history carrier is equivalent to both visible certificate presentations:
$$
\mathsf{TaggedOptionHistoryCarrier}_S(h)
\quad\Longleftrightarrow\quad
\mathsf{TaggedOptionHistoryPattern}_S(h)
$$
and
$$
\mathsf{TaggedOptionHistoryCarrier}_S(h)
\quad\Longleftrightarrow\quad
\mathsf{TaggedOptionHistoryLedger}_S(h).
$$
\end{theorem}
\begin{proof}
Unfold the three tagged option predicates. In the absent case, each presentation stores exactly the witness $\hsame(h,\emp)$, so the witness is reused unchanged in both directions. In the present case, each presentation stores the same payload history $a$ together with $S(a)$ and $\hsame(h,\Eone(a))$, so the same triple rebuilds the carrier, pattern, and ledger witnesses. The two cases exhaust the tagged option history carrier and the two visible certificate presentations.
\end{proof}

\begin{theorem}[Tagged option history carrier transport]
\label{thm:tagged-option-history-carrier-hsame-transport}
For any BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, if $\mathsf{TaggedOptionHistoryCarrier}_S(h)$ and $\hsame(h,k)$, then $\mathsf{TaggedOptionHistoryCarrier}_S(k)$.
\end{theorem}
\begin{proof}
Case-analyze the tagged carrier witness for $h$. In the absent case, compose the symmetry of $\hsame(h,k)$ with the stored endpoint witness $\hsame(h,\emp)$ to obtain $\hsame(k,\emp)$, then rebuild the absent clause. In the present case, keep the same payload $a$ and source witness $S(a)$. Compose the symmetry of $\hsame(h,k)$ with the stored endpoint witness $\hsame(h,\Eone(a))$ to obtain $\hsame(k,\Eone(a))$, then rebuild the present clause.
\end{proof}

\begin{theorem}[Tagged option history classifier stability fields]
\label{thm:tagged-option-history-constructor-exactness}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, source classifier $\sim_S$, source certificate $\mathsf{cert}:\NameCert(S,\sim_S)$, and $\mathsf{TaggedOptionSourceHsameCompatible}(S,\sim_S)$, the tagged option history carrier and classifier satisfy the following four stability fields:
\begin{enumerate}
  \item carrier-relative reflexivity: if $\mathsf{TaggedOptionHistoryCarrier}_S(h)$ holds, then $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,h)$ holds;
  \item classifier symmetry: if $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)$ holds, then $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(k,h)$ holds;
  \item classifier transitivity: if $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)$ and $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(k,u)$ hold, then $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,u)$ holds;
  \item classifier-induced carrier transport: if $\mathsf{TaggedOptionHistoryCarrier}_S(h)$ and $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(h,k)$ hold, then $\mathsf{TaggedOptionHistoryCarrier}_S(k)$ holds.
\end{enumerate}
\end{theorem}
\begin{proof}
For reflexivity, case-analyze the carrier witness. The absent case rebuilds the absent classifier branch from the stored empty endpoint witness and reflexivity, symmetry, and transitivity of $\hsame$; the present case keeps the same payload and applies the reflexivity field of $\mathsf{cert}$ to the source carrier witness. For symmetry, case-analyze the tagged classifier witness. The absent branch reverses the stored endpoint links by symmetry of $\hsame$, and the present branch reverses the payload classifier with $\mathsf{cert.equiv\_symm}$ while swapping the two endpoint witnesses. For transitivity, the absent branch composes empty endpoint witnesses. In the present-present branch, invert the two classifier witnesses around the shared middle history to obtain endpoint witnesses for $\Eone(b)$ and $\Eone(b')$. Symmetry and transitivity of $\hsame$ yield $\hsame(\Eone(b),\Eone(b'))$, $e1$-constructor inversion yields $\hsame(b,b')$, and source hsame compatibility gives $b\sim_S b'$. The field $\mathsf{cert.equiv\_trans}$ then composes $a\sim_S b$, $b\sim_S b'$, and $b'\sim_S c$ into $a\sim_S c$. For carrier transport, case-analyze the classifier witness; the absent branch gives the empty endpoint carrier, and the present branch stores the target payload carrier directly. Same-tag exactness, absent endpoint exactness, and mixed constructor separation are isolated in Theorems~\ref{thm:tagged-option-history-same-tag-exactness}, \ref{thm:tagged-option-history-absent-exactness}, and \ref{thm:tagged-option-history-mixed-tag-separation}.
\end{proof}

\begin{theorem}[Tagged option history same-tag exactness]
\label{thm:tagged-option-history-same-tag-exactness}
For a BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$ and source classifier $\sim_S$, the classifier $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}$ from Definition~\ref{def:tagged-option-history-classifier} is exact on equal visible tags:
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,k)
\quad\Longleftrightarrow\quad
\hsame(k,\emp)
$$
and
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\Eone(k))
\quad\Longleftrightarrow\quad
\exists a,b.\; S(a)\land S(b)\land \hsame(h,a)\land \hsame(k,b)\land a\sim_S b.
$$
\end{theorem}
\begin{proof}
For the absent endpoint, case-analyze the tagged classifier. The absent-absent branch stores $\hsame(k,\emp)$, while the present-present branch would contain $\hsame(\emp,\Eone(a))$ and is eliminated by empty-versus-one no-confusion. Conversely, $\hsame(k,\emp)$ combines with reflexivity of $\hsame(\emp,\emp)$ to build the absent-absent classifier branch.

For the present endpoint, the absent-absent branch would contain $\hsame(\Eone(h),\emp)$ and is eliminated by one-versus-empty no-confusion. The present-present branch gives payload histories $a,b$, source witnesses $S(a)$ and $S(b)$, a source classifier witness $a\sim_S b$, and endpoint witnesses $\hsame(\Eone(h),\Eone(a))$ and $\hsame(\Eone(k),\Eone(b))$; one-constructor inversion turns these endpoint witnesses into $\hsame(h,a)$ and $\hsame(k,b)$. Conversely, such payload data rebuilds the present-present classifier branch after applying the one-constructor congruence for $\hsame$ to the two payload endpoint witnesses.
\end{proof}

\begin{theorem}[Tagged option history absent exactness]
\label{thm:tagged-option-history-absent-exactness}
For every BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$, source classifier $\sim_S$, and history $k$, the tagged option history classifier has the exact absent endpoint:
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,k)
\quad\Longleftrightarrow\quad
\hsame(k,\emp).
$$
\end{theorem}
\begin{proof}
For the forward direction, case-analyze the classifier witness. The absent-absent case directly provides the endpoint witness $\hsame(k,\emp)$. The present-present case would classify $\emp$ with some $\Eone(a)$ endpoint, contradicting the BEDC empty-vs-$\Eone$ no-confusion theorem. For the reverse direction, combine the assumed $\hsame(k,\emp)$ with reflexivity of $\hsame$ at $\emp$ and rebuild the absent-absent classifier clause.
\end{proof}

\begin{theorem}[Tagged option history mixed-tag separation]
\label{thm:tagged-option-history-mixed-tag-separation}
For every BEDC history source carrier $S:\mathsf{BHist}\to\mathsf{Prop}$,
source classifier $\sim_S$, and histories $h,k$, both mixed constructor cases
are impossible:
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,\Eone(k))\to\bot
$$
and
$$
\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\emp)\to\bot.
$$
\end{theorem}
\begin{proof}
Case-analyze the tagged classifier witness. For
$\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\emp,\Eone(k))$, the
absent-absent branch forces $\hsame(\Eone(k),\emp)$, while the present-present
branch forces an endpoint witness from $\emp$ to some $\Eone(a)$. Both
contradict BEDC history no-confusion between empty and one-extension
constructors. The case
$\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}(\Eone(h),\emp)$ is
identical with the visible endpoints exchanged: the absent-absent branch forces
$\hsame(\Eone(h),\emp)$, and the present-present branch forces an endpoint
witness from $\emp$ to a present endpoint.
\end{proof}

\begin{theorem}[Tagged option history semantic certificate target]
\label{thm:tagged-option-history-semantic-certificate}
Let $S:\mathsf{BHist}\to\mathsf{Prop}$ be a source carrier, let $\sim_S$ be a source classifier on source histories, and assume a source $\NameCert(S,\sim_S)$ together with $\mathsf{TaggedOptionSourceHsameCompatible}(S,\sim_S)$. Then $\mathsf{TaggedOptionHistoryCarrier}_S$, $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}$, $\mathsf{TaggedOptionHistoryPattern}_S$, and $\mathsf{TaggedOptionHistoryLedger}_S$ form a $\mathsf{SemanticNameCert}$.
\end{theorem}
\begin{proof}
The absent branch supplies inhabitation through the empty history. Present reflexivity and symmetry are obtained by inverting the present classifier witness and applying the corresponding source certificate fields; the absent branch uses reflexivity, symmetry, and transitivity of $\hsame$ at $\emp$. For present-present transitivity, unpack the two classifier witnesses into payload data $(a,b)$ and $(b',c)$. The shared middle history has endpoint witnesses $\hsame(m,\Eone(b))$ and $\hsame(m,\Eone(b'))$, so symmetry and transitivity of $\hsame$ give $\hsame(\Eone(b),\Eone(b'))$. Applying $e1$-constructor inversion gives $\hsame(b,b')$; source hsame compatibility classifies the two middle payload presentations as $b\sim_S b'$. The source certificate transitivity field first composes $a\sim_S b$ with $b\sim_S b'$, then composes the result with $b'\sim_S c$. Theorems~\ref{thm:tagged-option-history-mixed-tag-separation} and \ref{thm:tagged-option-history-same-tag-exactness} eliminate mixed absent-present classifications and invert present-present classifications to payload histories. Carrier transport follows by cases on $\mathsf{TaggedOptionHistoryClassifier}_{S,\sim_S}$: absent transport uses the empty endpoint case, and present transport uses the $S(b)$ field already stored in the present-present classifier case. The visible tag pattern and visible tag ledger fields are supplied by Theorem~\ref{thm:tagged-option-history-carrier-pattern-ledger-equivalence}, which identifies both certificate presentations with the tagged option history carrier.
\end{proof}

\begin{corollary}[Tagged option history certificate over hsame]
\label{cor:tagged-option-history-semantic-certificate-hsame}
Let $S:\mathsf{BHist}\to\mathsf{Prop}$ be a source carrier. If a source $\NameCert(S,\hsame)$ is supplied, then $\mathsf{TaggedOptionHistoryCarrier}_S$, $\mathsf{TaggedOptionHistoryClassifier}_{S,\hsame}$, $\mathsf{TaggedOptionHistoryPattern}_S$, and $\mathsf{TaggedOptionHistoryLedger}_S$ form a $\mathsf{SemanticNameCert}$ with no separate compatibility hypothesis.
\end{corollary}
\begin{proof}
Apply Theorem~\ref{thm:tagged-option-history-semantic-certificate} with source classifier $\hsame$. The required compatibility input is exactly Theorem~\ref{thm:tagged-option-source-hsame-compatibility-hsame}.
\end{proof}

\begin{theorem}[Option history classifier endpoint transport]
\label{thm:option-history-classifier-hsame-transport}
If the optional history classifier relates \(h\) to \(k\), and
\(\hsame(h,h')\) and \(\hsame(k,k')\), then it relates \(h'\) to \(k'\).
\end{theorem}
\begin{proof}
Unpack the classifier into its endpoint carrier witnesses and the stored
\(\hsame(h,k)\) link. Transport both carriers along the endpoint sameness
links, then compose symmetry of \(\hsame(h,h')\), the stored link, and
\(\hsame(k,k')\).
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryClassifier\_hsame\_transport}

\begin{theorem}[Option history classifier symmetry]
\label{thm:option-history-classifier-symmetry}
For any source predicate on BEDC histories, the optional history classifier is
symmetric.
\end{theorem}
\begin{proof}
Unpack the classifier into endpoint carrier witnesses and the stored
\(\hsame(h,k)\) link. Swap the endpoint witnesses and reverse the stored link
by symmetry of \(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryClassifier\_symm}

\begin{theorem}[Option history classifier transitivity]
\label{thm:option-history-classifier-transitivity}
For any source predicate on BEDC histories, the optional history classifier is
transitive.
\end{theorem}
\begin{proof}
Unpack the two classifier witnesses. The source and target carrier witnesses
are preserved, and the underlying \(\hsame\) links compose across the shared
middle history.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryClassifier\_trans}

\begin{theorem}[Option history classifier empty left iff]
\label{thm:option-history-classifier-empty-left-iff}
For any source predicate on BEDC histories, the optional history classifier
relates the empty history on the left to \(k\) exactly when \(k\) is
history-same as the empty history.
\end{theorem}
\begin{proof}
In the forward direction, unpack the classifier and reverse its stored
\(\hsame(\emp,k)\) link. In the reverse direction, both endpoint carrier
witnesses are supplied by the absent-history branch, and the classifier link is
the symmetric form of the assumed \(\hsame(k,\emp)\).
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryClassifier\_empty\_left\_iff}

\begin{theorem}[Option classifier \(\hsame\) symmetry]
\label{thm:option-classifier-hsame-symm}
For optional BEDC histories, the option classifier induced by \(\hsame\) is symmetric.
\end{theorem}
\begin{proof}
The none--none case returns the existing classifier witness. The mixed constructor cases contradict the classifier definition, and the some--some case reverses the underlying BEDC history witness by \(\hsame\) symmetry.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionClassifierSpec\_hsame\_symm}

\begin{definition}[Option stability certificate]
\label{def:option-stability-certificate}
The stability certificate separates the typed optional classifier fields from
the nullable history-envelope fields.

For the typed $\mathsf{OptionClassifierSpec}$ classifier, the fields are:
\begin{enumerate}
  \item reflexivity for $\mathsf{none}$;
  \item reflexivity for $\mathsf{some}(a)$ from source reflexivity;
  \item transitivity from a source-transitivity hypothesis;
  \item no-confusion between $\mathsf{none}$ and $\mathsf{some}(a)$ in either order;
  \item present inversion, exposing the source classifier witness from a $\mathsf{some}$--$\mathsf{some}$ classification.
\end{enumerate}
Symmetry for this typed classifier is supplied only from a source-symmetry
hypothesis; the checked optional-history instance specializes that principle to
heads classified by $\hsame$.

For the nullable $\mathsf{OptionHistoryCarrier}$ envelope and its
$\mathsf{OptionHistoryClassifier}$, the certificate fields are:
\begin{enumerate}
  \item carrier transport across $\hsame$;
  \item endpoint transport for the classifier across $\hsame$ on both endpoints;
  \item classifier symmetry;
  \item classifier transitivity;
  \item ledger transport across raw and visible endpoint $\hsame$ links.
\end{enumerate}
\end{definition}
\leanchecked{BEDC.Derived.OptionUp.option\_stability\_certificate\_fields}

\begin{theorem}[Option classifier transitivity]
\label{thm:option-classifier-transitivity}
Let $R : A \to A \to \mathsf{Prop}$ be a source classifier relation.  If $R$
is transitive, then for optional carriers $x$, $y$, and $z$,
$$
  \mathsf{OptionClassifierSpec}(R,x,y)
  \quad\text{and}\quad
  \mathsf{OptionClassifierSpec}(R,y,z)
$$
imply $\mathsf{OptionClassifierSpec}(R,x,z)$.
\end{theorem}
\leanchecked{BEDC.Derived.OptionUp.OptionClassifierSpec\_trans}
\begin{proof}
Proceed by constructor case analysis on $x$, $y$, and $z$.  The none--none--none
case is immediate, mixed none--some cases contradict the classifier clauses, and
the some--some--some case is exactly the supplied transitivity of $R$.
\end{proof}

\begin{definition}[Option ledger policy]
\label{def:option-ledger-policy}
The ledger keeps a raw optional-history carrier witness and an $\hsame$ link from the raw history to the visible history.
\end{definition}
\leandef{BEDC.Derived.OptionUp.OptionHistoryLedgerPolicy}

\begin{theorem}[Option visible ledger carrier]
\label{thm:option-ledger-policy-visible-carrier}
If source-history membership transports across $\hsame$, then every option ledger policy exposes a visible optional-history carrier witness.
\end{theorem}
\begin{proof}
Unpack the raw carrier and the raw-to-visible history link. In the absent case, compose the symmetric visible-to-raw link with the raw empty-history witness. In the present case, transport the raw source witness along the raw-to-visible link.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryLedgerPolicy\_visible\_carrier}

\begin{theorem}[Option raw-visible ledger classifier]
\label{thm:option-ledger-raw-visible-classifier}
If source-history membership transports across $\hsame$, then every option
ledger policy classifies its raw history with its visible history.
\end{theorem}
\begin{proof}
Unpack the ledger into the raw carrier witness and the raw-to-visible
history-sameness link. The visible carrier is obtained from the visible-carrier
theorem, and the stored link supplies the classifier equality field.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryLedgerPolicy\_raw\_visible\_classifier}

\begin{theorem}[Option ledger history-same transport]
\label{thm:option-ledger-hsame-transport}
If both raw histories and both visible histories are related by $\hsame$, then
an option ledger policy transports from the first raw-visible pair to the
second.
\end{theorem}
\begin{proof}
Unpack the ledger into its raw carrier witness and raw-to-visible history link.
The raw carrier transports along the raw $\hsame$ witness. The transported
raw-to-visible link is the composite of the symmetric raw link, the stored
ledger link, and the visible link.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.OptionHistoryLedgerPolicy\_hsame\_transport}

\begin{theorem}[Concrete optional-history semantic certificate]
\label{thm:concrete-option-namecert}
For any source predicate on BEDC histories, $\mathsf{OptionHistoryCarrier}$ and $\mathsf{OptionHistoryClassifier}$ form the checked $\mathsf{SemanticNameCert}$ for the nullable empty-or-source history envelope. This semantic certificate does not assert constructor-discriminating history tags; that stronger tagged interface is the preceding paper-side target.
\end{theorem}
\begin{proof}
The history carrier contains the empty history and any source history. The classifier records both endpoint envelope-carrier witnesses and the BEDC history equality witness. Reflexivity, symmetry, transitivity, and carrier transport are the corresponding \(\hsame\) fields, while pattern and ledger soundness are carrier projections for the envelope.
\end{proof}
\leanchecked{BEDC.Derived.OptionUp.option\_history\_semantic\_name\_certificate}

\begin{corollary}[OptionUp certificate scope]
\label{cor:option-certificate-scope}
The checked envelope semantic certificate licenses the empty-or-source history
envelope only. It is not a checked constructor-tagged $\OptionUp$ certificate:
citations to Theorem~\ref{thm:concrete-option-namecert} assert the nullable
history-envelope certificate, while the explicit optional value interface is
licensed only when the typed tag classifier $\mathsf{OptionClassifierSpec}$,
none/some no-confusion, some-inversion, and the tag-plus-source ledger are
supplied together with that envelope.
\end{corollary}
