\chapter{A Concrete Naming Certificate for \(\ProdUp\)}
\label{ch:concrete-instances-prod-namecert}

The product interface $\ProdUp$ has two classifier levels plus the checked envelope. $\mathsf{ProdClassifierSpec}$ is the typed finite-pair helper. $\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}$ is the public BEDC-history certificate classifier induced by $\mathsf{ProdPairRep}$ and the source classifiers, while $\mathsf{ProdHistoryClassifier}$ is the checked envelope classifier using endpoint $\hsame$. It is licensed only as a derived constructor over the two sources.

\section{Roadmap template status}

\begin{enumerate}
  \item \textbf{Traditional target}: ordered product data with one left component and one right component.
  \item \textbf{BEDC source}: the checked history-envelope certificate uses inhabited source-history predicates $L$ and $R$; the explicit typed interface uses two licensed source carriers $A$ and $B$, each with its own name certificate.
  \item \textbf{Carrier choice}: the paired history carrier records a left history, a right history, and the continuation that combines them.
  \item \textbf{Classifier choice}: $\mathsf{ProdClassifierSpec}$ is the typed finite-pair helper; $\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}$ is the public history-level classifier from $\mathsf{ProdPairRep}$ and source classifiers; $\mathsf{ProdHistoryClassifier}$ is the checked envelope classifier using endpoint $\hsame$.
  \item \textbf{Stability obligations}: component transport, continuation transport, unary closure from components, history-envelope classifier symmetry and transitivity, typed classifier symmetry and transitivity, typed coordinate inversion, $\mathsf{ProdPairRepCoherent}$, and componentwise-to-envelope descent.
  \item \textbf{Ledger}: no product quotient is used; pairing records both component witnesses, their generated continuation, and the displayed pair ledger soundness needed by the public history-level certificate.
  \item \textbf{Core theorem list}: append introduction, continuation introduction, carrier transport, unary closure, classifier equivalence, component-envelope inversion, $\mathsf{ProdPairRepCoherent}$ criteria, displayed pair ledger soundness, componentwise-to-envelope descent under $\hsame$-sound source classifiers, and the semantic name certificate.
  \item \textbf{Exactness predicate}: typed classification holds exactly when both finite-pair coordinates classify in their respective sources; public history-level classification holds through displayed $\mathsf{ProdPairRep}$ components and source classifiers; envelope classification uses endpoint $\hsame$.
  \item \textbf{Standard bridge}: the checked history-envelope bridge reads back only as a generated product endpoint with a displayed pair representation. Ordinary ordered-pair and componentwise history readback belong to the componentwise certificate target under $\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ and $\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}$.
  \item \textbf{Status}: Theorem~\ref{thm:concrete-prod-namecert} is the checked history-envelope certificate via $\mathsf{BEDC.Derived.ProdUp.prod\_history\_semantic\_name\_certificate}$. The Phase Finite Data public-object product scope remains a $\mathsf{ProofTarget}$ at Theorem~\ref{thm:prod-component-history-semantic-certificate-target} until the componentwise classifier, $\mathsf{ProdPairRepCoherent}$ field, displayed pair ledger, and descent comparison are machine-checked.
\end{enumerate}

\section{Carrier definition}

\begin{definition}[Prod carrier]
\label{def:prod-carrier}
For licensed source carriers \(A\) and \(B\), define a pair carrier with constructor \(\mathsf{pair}(a,b)\).
\end{definition}
\leandef{BEDC.Derived.ProdUp.ProdCarrier}

\section{The certificate}

\begin{definition}[Prod source specification]
\label{def:prod-source-specification}
For the checked history-envelope certificate, the source specification is a
pair of inhabited predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$. The carrier
is $\mathsf{ProdHistoryCarrier}(L,R)$, and the classifier is
$\mathsf{ProdHistoryClassifier}(L,R)$; no source $\NameCert$ is required at
this scope.

For the explicit ordered-product interface, the source data are two licensed
carriers with $\NameCert$ witnesses. Those certificates are used for typed
component transport, pair-representation coherence, and displayed component-exposure fields.
\end{definition}
\leandef{BEDC.Derived.ProdUp.ProdHistoryCarrier}

\begin{theorem}[Product history carrier append introduction]
\label{thm:prod-history-carrier-append-intro}
If \(l\) lies in the left source carrier and \(r\) lies in the right source
carrier, then \(\mathsf{append}(l,r)\) lies in the product history carrier.
\end{theorem}
\begin{proof}
Use \(l\) and \(r\) as the two component witnesses. The BEDC continuation
judgment is witnessed by reflexivity of the defining append result, so the
product history carrier is rebuilt from the two source proofs and that
continuation witness.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryCarrier\_append\_intro}

\begin{theorem}[Product history carrier continuation introduction]
\label{thm:prod-history-carrier-cont-intro}
If \(l\) lies in the left source carrier, \(r\) lies in the right source
carrier, and \(\Cont(l,r,h)\), then \(h\) lies in the product history carrier.
\end{theorem}
\begin{proof}
Use \(l\) and \(r\) as the component witnesses. The supplied continuation
proof is exactly the result witness required by the product history carrier.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryCarrier\_cont\_intro}

\begin{theorem}[Product unary history closure]
\label{thm:prod-history-carrier-unary}
If a product history is generated from unary left and right histories, then the
resulting product history is unary.
\end{theorem}
\begin{proof}
Invert the product-history carrier into its left history, right history, unary
component witnesses, and continuation proof. Unary closure under continuation
turns the two unary component witnesses and the stored continuation proof into
unary membership of the result history.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryCarrier\_unary}

\begin{theorem}[Product history carrier transport]
\label{thm:prod-history-carrier-hsame-transport}
If two product histories are internally the same and the first is generated from a left witness, a right witness, and a continuation proof, then the second is generated from the same component witnesses and the transported continuation proof.
\end{theorem}
\begin{proof}
Invert the product-history carrier into its left history, right history, component witnesses, and continuation proof. Transport the continuation result across \(\hsame\), and rebuild the product-history carrier with the same component witnesses.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryCarrier\_hsame\_transport}

\begin{theorem}[Product history carrier unary from components]
\label{thm:prod-history-carrier-unary-of-components}
If the left and right source predicates each determine unary histories, then
every product-history carrier generated from those predicates is unary.
\end{theorem}
\begin{proof}
Unpack the product-history carrier into component histories \(l\) and \(r\),
their source witnesses, and the BEDC continuation witness for the result.
The component assumptions give unary witnesses for \(l\) and \(r\), and BEDC
unary continuation closure gives unary membership of the product result.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryCarrier\_unary\_of\_components}

\begin{definition}[Prod pattern specification]
\label{def:prod-pattern-specification}
The pattern is paired generation from one \(A\)-witness and one \(B\)-witness.
\end{definition}

\begin{definition}[Prod classifier specification]
\label{def:prod-classifier-specification}
The typed classifier $\mathsf{ProdClassifierSpec}$ relates pairs componentwise using the classifiers of $A$ and $B$. The typed wrapper $\mathsf{ProdClassifier}$ has the same componentwise content. Separately, the checked history-level scope is $\mathsf{ProdHistoryClassifier}(L,R)$: it relates histories $h$ and $k$ exactly when $h$ lies in $\mathsf{ProdHistoryCarrier}(L,R)$, $k$ lies in $\mathsf{ProdHistoryCarrier}(L,R)$, and $\hsame(h,k)$ holds.
\end{definition}
\leandef{BEDC.Derived.ProdUp.ProdClassifierSpec}
\leandef{BEDC.Derived.ProdUp.ProdHistoryClassifier}

\begin{theorem}[Product typed classifier coordinate exactness]
\label{thm:prod-classifier-coordinate-exactness}
For types $A$ and $B$, component classifiers $R_A:A\to A\to\mathsf{Prop}$
and $R_B:B\to B\to\mathsf{Prop}$, and elements $a,a':A$ and $b,b':B$,
the product typed classifier is exact on coordinates:
$$
\mathsf{ProdClassifierSpec}(R_A,R_B,\mathsf{pair}(a,b),\mathsf{pair}(a',b'))
\quad\Longleftrightarrow\quad
R_A(a,a')\land R_B(b,b').
$$
\end{theorem}
\begin{proof}
Unfold $\mathsf{ProdClassifierSpec}$. The forward direction is constructor
inversion on the product classifier witness, yielding the two coordinate
witnesses. The reverse direction pairs the two displayed coordinate witnesses
to rebuild the product classifier witness.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.prodClassifier\_iff}

\begin{definition}[Product typed source carrier]
\label{def:product-typed-source-carrier}
For source carriers $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and
$x:\mathsf{ProdCarrier}(\mathsf{BHist},\mathsf{BHist})$, define
$\mathsf{ProdTypedCarrier}_{L,R}(x)$ by the displayed pair decomposition
$$
\mathsf{ProdTypedCarrier}_{L,R}(x)
\quad\Longleftrightarrow\quad
\exists l,r:\mathsf{BHist}.\ x=\mathsf{pair}(l,r)\land L(l)\land R(r).
$$
It is the typed source-carrier predicate for the explicit ordered-product
interface: the left coordinate is licensed by $L$ and the right coordinate is
licensed by $R$.
\end{definition}

\begin{theorem}[Product typed carrier transport from source certificates]
\label{thm:product-typed-carrier-transport-source-certificates}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source carriers and let
$\sim_L,\sim_R$ be source classifiers. If
$\mathsf{cert}_L:\NameCert(L,\sim_L)$,
$\mathsf{cert}_R:\NameCert(R,\sim_R)$,
$x,y:\mathsf{ProdCarrier}(\mathsf{BHist},\mathsf{BHist})$,
$\mathsf{ProdTypedCarrier}_{L,R}(x)$, and
$\mathsf{ProdClassifierSpec}(\sim_L,\sim_R,x,y)$, then
$\mathsf{ProdTypedCarrier}_{L,R}(y)$.
\end{theorem}
\begin{proof}
Invert the typed carrier witness for $x$ to obtain coordinates $l$ and $r$
with $x=\mathsf{pair}(l,r)$, $L(l)$, and $R(r)$. Invert the product carrier
$y$ as $\mathsf{pair}(l',r')$. Apply
Theorem~\ref{thm:prod-classifier-coordinate-exactness} to the classifier
witness for the two displayed pairs; this yields source classifier witnesses
$l\sim_L l'$ and $r\sim_R r'$. The
$\mathsf{carrier\_respects\_equiv}$ fields of $\mathsf{cert}_L$ and
$\mathsf{cert}_R$ transport $L(l)$ to $L(l')$ and $R(r)$ to $R(r')$.
Those transported witnesses rebuild $\mathsf{ProdTypedCarrier}_{L,R}(y)$.
\end{proof}

\begin{theorem}[Product history classifier endpoint carrier exposure]
\label{thm:prod-history-classifier-component-inversion}
For all source predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and histories
$h,k:\mathsf{BHist}$, the following equivalence holds:
$$
\mathsf{ProdHistoryClassifier}(L,R,h,k)
\Longleftrightarrow
\exists l,r,l',r':\mathsf{BHist},\;
L(l)\land R(r)\land \Cont(l,r,h)\land
L(l')\land R(r')\land \Cont(l',r',k)\land \hsame(h,k).
$$
Componentwise equality and componentwise classification belong to
$\mathsf{ProdClassifierSpec}$, not to the history-envelope classifier.
\end{theorem}
\begin{proof}
For the forward direction of the displayed equivalence, unfold
$\mathsf{ProdHistoryClassifier}$. Its two endpoint premises are
$\mathsf{ProdHistoryCarrier}(L,R,h)$ and
$\mathsf{ProdHistoryCarrier}(L,R,k)$, and each carrier premise unfolds into
one left witness, one right witness, the two source-membership proofs, and the
continuation proof producing the visible endpoint. Pair those two carrier
inversions with the stored $\hsame(h,k)$ witness for the forward direction.
Conversely, the displayed data rebuild the two product-history carrier
premises and then the classifier witness for the reverse direction of the
equivalence. The result is endpoint exposure rather than coordinate
projection.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_component\_inversion}

\begin{theorem}[Product history source monotonicity]
\label{thm:prod-history-source-monotonicity}
The roadmap-template fit is: traditional target ordered-product stability
under source refinement; BEDC source $\mathsf{BHist}$ with $\Cont$; carrier
$\mathsf{ProdHistoryCarrier}$; classifier $\mathsf{ProdHistoryClassifier}$;
stability obligation source inclusion transport; ledger unchanged
pair-continuation evidence; core theorem list carrier monotonicity plus
classifier monotonicity; exactness predicate preservation of visible product
endpoints under source refinement; standard bridge ordinary product source
restriction; status $\mathsf{ProofTarget}$.

For predicates $L,R,L',R':\mathsf{BHist}\to\mathsf{Prop}$, suppose
$\forall h.\; L(h)\to L'(h)$ and $\forall h.\; R(h)\to R'(h)$. Then every
$\mathsf{ProdHistoryCarrier}(L,R,h)$ yields
$\mathsf{ProdHistoryCarrier}(L',R',h)$. Under the same hypotheses, every
$\mathsf{ProdHistoryClassifier}(L,R,h,k)$ yields
$\mathsf{ProdHistoryClassifier}(L',R',h,k)$.
\end{theorem}
\begin{proof}
For the carrier clause, unpack the product carrier into histories $l$ and $r$,
source witnesses $L(l)$ and $R(r)$, and the continuation witness
$\Cont(l,r,h)$. Apply the two source inclusions to obtain $L'(l)$ and $R'(r)$,
then rebuild $\mathsf{ProdHistoryCarrier}(L',R',h)$ with the same continuation
evidence.

For the classifier clause, unfold the stored classifier data. Apply the carrier
clause to both endpoint carriers, and keep the stored $\hsame(h,k)$ witness
unchanged to rebuild $\mathsf{ProdHistoryClassifier}(L',R',h,k)$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistorySource\_monotonicity}

\begin{theorem}[Product history source equivalence]
\label{thm:prod-history-source-equivalence}
The roadmap-template fit is: traditional target ordered-product envelope
invariance under equivalent source presentations; BEDC source $\mathsf{BHist}$
with $\Cont$; carrier $\mathsf{ProdHistoryCarrier}$; classifier
$\mathsf{ProdHistoryClassifier}$; stability obligation source-presentation
equivalence; ledger unchanged continuation evidence; exactness preservation of
the visible product endpoints; standard bridge unchanged ordered-pair readback;
status $\mathsf{ProofTarget}$.

For predicates $L,R,L',R':\mathsf{BHist}\to\mathsf{Prop}$, suppose
$\forall h.\; L(h)\leftrightarrow L'(h)$ and
$\forall h.\; R(h)\leftrightarrow R'(h)$. Then for every history $h$,
$\mathsf{ProdHistoryCarrier}(L,R,h)$ holds exactly when
$\mathsf{ProdHistoryCarrier}(L',R',h)$ holds. Under the same hypotheses, for
every pair of histories $h,k$, $\mathsf{ProdHistoryClassifier}(L,R,h,k)$ holds
exactly when $\mathsf{ProdHistoryClassifier}(L',R',h,k)$ holds.
\end{theorem}
\begin{proof}
Apply \autoref{thm:prod-history-source-monotonicity} from left to right using
the forward halves of the two source equivalences. This gives the carrier
implication and the classifier implication from $(L,R)$ to $(L',R')$ with the
same continuation evidence and the same $\hsame$ endpoint witness. Apply the
same monotonicity theorem from right to left using the reverse halves of the two
source equivalences. Pair the two implications for the carrier clause and pair
the two implications for the classifier clause.
\end{proof}

\begin{theorem}[Product history classifier right transport]
\label{thm:prod-history-classifier-right-hsame-transport}
If a product-history classifier relates $h$ to $k$, and $k$ is internally the same as $k'$, then the classifier relates $h$ to $k'$.
\end{theorem}
\begin{proof}
Invert the product-history classifier into the left carrier, the right carrier, and the stored $\hsame(h,k)$ witness. Transport the right carrier across $\hsame(k,k')$, then compose $\hsame(h,k)$ with $\hsame(k,k')$ for the classifier witness.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_right\_hsame\_transport}

\begin{theorem}[Product history classifier endpoint transport]
\label{thm:prod-history-classifier-hsame-transport}
If a product-history classifier relates $h$ to $k$, and $h$ is internally the same as $h'$ while $k$ is internally the same as $k'$, then the classifier relates $h'$ to $k'$.
\end{theorem}
\begin{proof}
Invert the product-history classifier into endpoint carriers and the stored $\hsame(h,k)$ witness. Transport both endpoint carriers across their respective $\hsame$ witnesses, then compose symmetry of $\hsame(h,h')$, the stored link, and $\hsame(k,k')$ to obtain $\hsame(h',k')$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_hsame\_transport}

\begin{theorem}[Product history classifier symmetry]
\label{thm:prod-history-classifier-symmetry}
If a product-history classifier relates \(h\) to \(k\), then it relates
\(k\) to \(h\).
\end{theorem}
\begin{proof}
Unpack the classifier into the two endpoint product carriers and the stored
\(\hsame(h,k)\) link. Exchange the endpoint carriers and reverse the stored
history-sameness link by symmetry.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_symm}

\begin{theorem}[Product history classifier left transport]
\label{thm:prod-history-classifier-left-hsame-transport}
If a product-history classifier relates $h$ to $k$, and $h$ is internally the
same as $h'$, then the classifier relates $h'$ to $k$.
\end{theorem}
\begin{proof}
Invert the classifier witness. Transport the left carrier through the
$\hsame(h,h')$ witness, keep the right carrier, and compose the symmetric
$\hsame(h',h)$ link with the stored $\hsame(h,k)$ classifier witness.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_left\_hsame\_transport}

\begin{theorem}[Product history classifier transitivity]
\label{thm:prod-history-classifier-transitivity}
For source-history predicates $L$ and $R$ on $\mathsf{BHist}$, if $\mathsf{ProdHistoryClassifier}(L,R,h,k)$ and $\mathsf{ProdHistoryClassifier}(L,R,k,u)$, then $\mathsf{ProdHistoryClassifier}(L,R,h,u)$.
\end{theorem}
\begin{proof}
Unpack the endpoint $\mathsf{ProdHistoryCarrier}(L,R)$ witnesses for $h$ and $k$ from the first classifier witness, and for $k$ and $u$ from the second. Keep the $h$ endpoint carrier from the first witness and the $u$ endpoint carrier from the second, compose the stored $\hsame(h,k)$ and $\hsame(k,u)$ links, and rebuild $\mathsf{ProdHistoryClassifier}(L,R,h,u)$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_trans}

\begin{theorem}[Product history classifier continuation congruence]
\label{thm:prod-history-classifier-cont-congr}
Let $L$ and $R$ be source-history predicates on $\mathsf{BHist}$. Assume the left and right transport fields
$$
\forall x\,y.\; L(x)\land\hsame(x,y)\to L(y)
$$
and
$$
\forall x\,y.\; R(x)\land\hsame(x,y)\to R(y).
$$
If $L(l)$, $R(r)$, $\hsame(l,l')$, $\hsame(r,r')$, $\Cont(l,r,h)$, and $\Cont(l',r',h')$, then
$\mathsf{ProdHistoryClassifier}(L,R,h,h')$.
\end{theorem}
\begin{proof}
Apply the displayed left transport field to $L(l)$ and $\hsame(l,l')$ to obtain $L(l')$, and apply the displayed right transport field to $R(r)$ and $\hsame(r,r')$ to obtain $R(r')$. Product history carrier continuation introduction builds endpoint carrier witnesses for $h$ and $h'$ from the two continuation witnesses. Continuation respect for $\hsame$ transports the result endpoints across the two component links, yielding $\hsame(h,h')$. These three pieces are exactly the history-envelope classifier fields.
\end{proof}

\begin{definition}[Product pair representation]
\label{def:prod-pair-rep}
For source-history predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$, define
$\mathsf{ProdPairRep}_{L,R}(h,l,r)$ to mean that $l$ is a left source
history, $r$ is a right source history, and their continuation presents $h$:
$$
  \mathsf{ProdPairRep}_{L,R}(h,l,r)
  \quad:\Longleftrightarrow\quad
  L(l)\wedge R(r)\wedge \Cont(l,r,h).
$$
\end{definition}
\leandef{BEDC.Derived.ProdUp.ProdPairRep}

\begin{theorem}[Product pair representation coverage]
\label{thm:prod-pair-rep-coverage}
For source-history predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and history $h$,
$$
  \mathsf{ProdHistoryCarrier}(L,R,h)
  \quad\Longleftrightarrow\quad
  \exists l,r:\mathsf{BHist}.\;\mathsf{ProdPairRep}_{L,R}(h,l,r).
$$
\end{theorem}
\begin{proof}
Unfold $\mathsf{ProdHistoryCarrier}$ and $\mathsf{ProdPairRep}$. In the forward direction, the carrier witness exposes component histories $l$ and $r$, source witnesses $L(l)$ and $R(r)$, and the continuation witness $\Cont(l,r,h)$; these are exactly the displayed pair representation witnesses. In the reverse direction, a displayed pair representation supplies the same two component histories, source witnesses, and continuation witness, so it rebuilds the product history carrier witness for $h$.
\end{proof}

\begin{theorem}[Product pair representation endpoint transport]
\label{thm:prod-pair-rep-hsame-transport}
For source-history predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and histories
$h,k,l,r$, if $\mathsf{ProdPairRep}_{L,R}(h,l,r)$ and $\hsame(h,k)$, then
$\mathsf{ProdPairRep}_{L,R}(k,l,r)$ holds.
\end{theorem}
\begin{proof}
The per-object fit is: traditional target ordered-pair endpoint stability; BEDC
source $\mathsf{BHist}$ with $\Cont$; carrier $\mathsf{ProdPairRep}$;
classifier endpoint $\hsame$; stability obligation endpoint transport; ledger
displayed pair representation; core theorem this transport law; exactness pair
presentation preserved by endpoint sameness; standard bridge stable ordered-pair
endpoint; status $\mathsf{ProofTarget}$. Unfold $\mathsf{ProdPairRep}$ to keep
$L(l)$ and $R(r)$, and transport the $\Cont(l,r,h)$ result across $\hsame(h,k)$
using continuation result transport. The transported continuation witness
together with the unchanged source witnesses rebuilds
$\mathsf{ProdPairRep}_{L,R}(k,l,r)$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdPairRep\_hsame\_transport}

\begin{theorem}[Product fixed-pair endpoint determinism]
\label{thm:prod-pair-rep-determinism}
For source-history predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and histories $h,k,l,r$,
if $\mathsf{ProdPairRep}_{L,R}(h,l,r)$ and
$\mathsf{ProdPairRep}_{L,R}(k,l,r)$, then
$\hsame(h,k)$ holds, and consequently
$\mathsf{ProdHistoryClassifier}(L,R,h,k)$ holds.
\end{theorem}
\begin{proof}
Unfold both displayed pair representations. The first supplies $L(l)$, $R(r)$,
and $\Cont(l,r,h)$; the second supplies the same component source witnesses and
$\Cont(l,r,k)$. Applying continuation determinism to the two continuation
witnesses gives $\hsame(h,k)$. The same source witnesses and continuation
witnesses rebuild $\mathsf{ProdHistoryCarrier}(L,R,h)$ and
$\mathsf{ProdHistoryCarrier}(L,R,k)$, and these endpoint carriers together with
the $\hsame$ witness rebuild
$\mathsf{ProdHistoryClassifier}(L,R,h,k)$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdHistoryClassifier\_fixed\_pair\_determinism}
This statement fixes both component histories; comparison of two different pair presentations of one endpoint is exactly the separate coherence datum in Definition~\ref{def:prod-pair-rep-coherent}.

\begin{theorem}[Product fixed-pair endpoint exactness]
\label{thm:prod-pair-rep-fixed-endpoint-exactness}
For source-history predicates $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and histories
$h,k,l,r$, if $\mathsf{ProdPairRep}_{L,R}(h,l,r)$ holds, then
$$
  \mathsf{ProdPairRep}_{L,R}(k,l,r)\Longleftrightarrow\hsame(h,k).
$$
\end{theorem}
\begin{proof}
The per-object fit is: traditional target ordered-pair endpoint readback; BEDC
source $\mathsf{BHist}$ with $\Cont$; carrier $\mathsf{ProdPairRep}$;
classifier endpoint $\hsame$; stability by endpoint transport and continuation
determinism; ledger fixed displayed pair; core theorem fixed-pair endpoint
exactness; exactness predicate the displayed iff; standard bridge fixed
ordered-pair endpoint; status $\mathsf{ProofTarget}$. For the forward
direction, apply Theorem~\ref{thm:prod-pair-rep-determinism} to the displayed
base representation and the target representation, then project the
$\hsame(h,k)$ conjunct. For the reverse direction, apply
Theorem~\ref{thm:prod-pair-rep-hsame-transport} to the base representation and
the displayed endpoint sameness.
\end{proof}

\begin{definition}[Product pair-representation coherence]
\label{def:prod-pair-rep-coherent}
For source classifiers $\sim_L$ and $\sim_R$, define
$\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ to mean that any two pair
representations of the same product history classify their corresponding
components:
$$
  \forall h\,l\,r\,l'\,r'.\;
  \mathsf{ProdPairRep}_{L,R}(h,l,r)\wedge
  \mathsf{ProdPairRep}_{L,R}(h,l',r')
  \to (l\sim_L l')\wedge(r\sim_R r').
$$
\end{definition}

\begin{theorem}[Product raw pair representation coherence is not automatic]
\label{thm:prod-pair-rep-coherence-not-automatic}
Let $\mathsf{TopCarrier}(h):=\mathsf{True}$ for every $h:\mathsf{BHist}$, and take both source classifiers to be $\hsame$. Then $\neg\mathsf{ProdPairRepCoherent}_{\mathsf{TopCarrier},\mathsf{TopCarrier},\hsame,\hsame}$ holds.

The per-object fit is: traditional target ordered-pair readback; BEDC source $\mathsf{BHist}$ with $\Cont$ and $\hsame$; carrier $\mathsf{ProdPairRep}$; classifier $\hsame$; stability obligation coherence; ledger displayed pair boundary; core theorem non-automaticity; exactness obstruction; standard bridge raw append ambiguity; status $\mathsf{ProofTarget}$.
\end{theorem}
\begin{proof}
The endpoint $\Ezero(\emp)$ has two raw pair presentations under $\mathsf{TopCarrier}$. The left-unit presentation uses components $(\emp,\Ezero(\emp))$, and the right-unit presentation uses components $(\Ezero(\emp),\emp)$. If product pair-representation coherence were automatic for the two $\hsame$ classifiers, applying it to these two presentations of the same endpoint would force $\hsame(\emp,\Ezero(\emp))$ on the left components, and also $\hsame(\Ezero(\emp),\emp)$ on the right components. BEDC history no-confusion separates the empty history from a zero-step endpoint, so the forced $\hsame(\emp,\Ezero(\emp))$ is impossible. Thus the componentwise ordered-pair certificate needs displayed coherence data and cannot be recovered from raw continuation alone.
\end{proof}

\begin{definition}[Product componentwise history classifier]
\label{def:prod-component-history-classifier}
For source-history carriers $L,R:\mathsf{BHist}\to\mathsf{Prop}$ and source
classifiers $\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$,
define $\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}(h,k)$ by
the existence of component histories $l_h,r_h,l_k,r_k$ such that
$$
\mathsf{ProdPairRep}_{L,R}(h,l_h,r_h)
\wedge
\mathsf{ProdPairRep}_{L,R}(k,l_k,r_k)
\wedge
l_h\sim_L l_k
\wedge
r_h\sim_R r_k.
$$
\end{definition}
\leandef{BEDC.Derived.ProdUp.ProdComponentHistoryClassifier}

\begin{theorem}[Product componentwise history classifier source refinement]
\label{thm:prod-component-history-classifier-source-refinement}
The per-object fit is: traditional ordered-product classifier stability under
source refinement; BEDC source $\mathsf{BHist}$ with $\Cont$; carrier through
$\mathsf{ProdPairRep}$; classifier
$\mathsf{ProdComponentHistoryClassifier}$; ledger unchanged displayed pair
representations; one-way classifier preservation under carrier and classifier
inclusions; status $\mathsf{ProofTarget}$.

For carriers $L,R,L',R':\mathsf{BHist}\to\mathsf{Prop}$, classifiers
$\sim_L,\sim_R,\sim'_L,\sim'_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$,
and histories $h,k:\mathsf{BHist}$, suppose $\forall u.\;L(u)\to L'(u)$, $\forall u.\;R(u)\to R'(u)$,
$\forall x\,y.\;x\sim_L y\to x\sim'_L y$, and
$\forall x\,y.\;x\sim_R y\to x\sim'_R y$. Then
$\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}(h,k)$ implies
$\mathsf{ProdComponentHistoryClassifier}_{L',R',\sim'_L,\sim'_R}(h,k)$.
\end{theorem}
\begin{proof}
Unpack the componentwise classifier witness into displayed pair
representations of $h$ and $k$ with components $l_h,r_h,l_k,r_k$, together
with the two component classifier witnesses. Rebuild each displayed pair
representation for $L',R'$ by applying the carrier inclusions to the stored
component source witnesses and keeping the same continuation evidence.
Transport the two component classifier witnesses through the classifier
implications, then repack these two rebuilt displayed pair representations and
the transported component witnesses as a
$\mathsf{ProdComponentHistoryClassifier}_{L',R',\sim'_L,\sim'_R}(h,k)$
witness.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdComponentHistoryClassifier\_source\_refinement}

\input{parts/concrete_instances/09_prod_componentwise_history_classifier_endpoints}

\input{parts/concrete_instances/09_prod_componentwise_certificate_target}

\begin{theorem}[Product componentwise history classifier inversion]
\label{thm:prod-component-history-classifier-inversion}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers, let
$\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$ be their source
classifiers. Assume $\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ and the
displayed source transitivity laws
$$
\forall a\,b\,c.\;a\sim_L b\to b\sim_L c\to a\sim_L c
\qquad\hbox{and}\qquad
\forall a\,b\,c.\;a\sim_R b\to b\sim_R c\to a\sim_R c.
$$
If
$\mathsf{ProdPairRep}_{L,R}(h,l,r)$,
$\mathsf{ProdPairRep}_{L,R}(k,l',r')$, and
$\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}(h,k)$ hold, then
$l\sim_L l'$ and $r\sim_R r'$.
\end{theorem}
\begin{proof}
Unpack the componentwise classifier witness to obtain component histories
$l_h,r_h,l_k,r_k$ with pair representations for $h$ and $k$, together with
$l_h\sim_L l_k$ and $r_h\sim_R r_k$. Apply pair-representation coherence at
$h$ to the displayed representation $(l,r)$ and the witness representation
$(l_h,r_h)$, yielding $l\sim_L l_h$ and $r\sim_R r_h$. Apply coherence at
$k$ to the witness representation $(l_k,r_k)$ and the displayed
representation $(l',r')$, yielding $l_k\sim_L l'$ and $r_k\sim_R r'$. The
displayed source transitivity hypotheses compose the left chain
$l\sim_L l_h\sim_L l_k\sim_L l'$ and the right chain
$r\sim_R r_h\sim_R r_k\sim_R r'$.
\end{proof}

The descent theorem instantiates the roadmap template as traditional ordered-pair descent over the BEDC source $\mathsf{BHist}$ with $\Cont$, carrier $\mathsf{ProdHistoryCarrier}$, classifier bridge from componentwise to envelope under $\hsame$-sound source classifiers, ledger by displayed pair representations, and status $\mathsf{ProofTarget}$.

\begin{theorem}[Product componentwise history classifier descends to envelope]
\label{thm:prod-component-history-classifier-descends-to-envelope}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers and let
$\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$ be source
classifiers. Assume the source classifiers are $\hsame$-sound:
$$
\forall x\,y.\;x\sim_L y\to\hsame(x,y)
\qquad\hbox{and}\qquad
\forall x\,y.\;x\sim_R y\to\hsame(x,y).
$$
If $\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}(h,k)$ holds,
then $\mathsf{ProdHistoryClassifier}(L,R,h,k)$ holds.
\end{theorem}
\begin{proof}
Unpack the componentwise classifier into component histories
$l_h,r_h,l_k,r_k$, pair representations
$\mathsf{ProdPairRep}_{L,R}(h,l_h,r_h)$ and
$\mathsf{ProdPairRep}_{L,R}(k,l_k,r_k)$, and component links
$l_h\sim_L l_k$ and $r_h\sim_R r_k$. The two $\hsame$-sound assumptions turn
the component links into $\hsame(l_h,l_k)$ and $\hsame(r_h,r_k)$. The pair
representations expose $\Cont(l_h,r_h,h)$ and $\Cont(l_k,r_k,k)$, so
continuation respect for $\hsame$ yields $\hsame(h,k)$. Pair-representation
coverage rebuilds $\mathsf{ProdHistoryCarrier}(L,R,h)$ and
$\mathsf{ProdHistoryCarrier}(L,R,k)$ from the two displayed pair
representations, and these two endpoint carriers together with
$\hsame(h,k)$ rebuild $\mathsf{ProdHistoryClassifier}(L,R,h,k)$.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdComponentHistoryClassifier\_descends\_to\_envelope}

\begin{theorem}[Product envelope hsame classifier recovers componentwise classifier]
\label{thm:prod-history-envelope-to-componentwise-hsame}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers. Assume
$\mathsf{ProdPairRepCoherent}_{L,R,\hsame,\hsame}$. If
$\mathsf{ProdHistoryClassifier}(L,R,h,k)$ holds, then
$\mathsf{ProdComponentHistoryClassifier}_{L,R,\hsame,\hsame}(h,k)$ holds.
\end{theorem}
\begin{proof}
Unpack the envelope classifier into endpoint carrier witnesses for $h$ and
$k$ and an endpoint link $\hsame(h,k)$. Pair-representation coverage for the
two endpoint carriers supplies displayed pair representations
$\mathsf{ProdPairRep}_{L,R}(h,l_h,r_h)$ and
$\mathsf{ProdPairRep}_{L,R}(k,l_k,r_k)$. First reverse the endpoint link to
obtain $\hsame(k,h)$. Apply
Theorem~\ref{thm:prod-pair-rep-hsame-transport} to the displayed
representation of $k$ and this reversed link, producing a displayed pair
representation of $h$ with the same components $l_k,r_k$.
Pair-representation coherence at $h$ compares the two representations of $h$
and gives
$\hsame(l_h,l_k)$ and $\hsame(r_h,r_k)$. These two component links together
with the original displayed pair representations for $h$ and $k$ rebuild
$\mathsf{ProdComponentHistoryClassifier}_{L,R,\hsame,\hsame}(h,k)$.
\end{proof}

\begin{theorem}[Product envelope and componentwise hsame classifiers coincide]
\label{thm:prod-envelope-componentwise-hsame-classifiers-coincide}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers and assume
$\mathsf{ProdPairRepCoherent}_{L,R,\hsame,\hsame}$. For all
$h,k:\mathsf{BHist}$,
$$
\mathsf{ProdHistoryClassifier}(L,R,h,k)
\Longleftrightarrow
\mathsf{ProdComponentHistoryClassifier}_{L,R,\hsame,\hsame}(h,k).
$$
\end{theorem}
\begin{proof}
The forward implication is Theorem~\ref{thm:prod-history-envelope-to-componentwise-hsame}.
For the reverse implication, apply
Theorem~\ref{thm:prod-component-history-classifier-descends-to-envelope}
with both source classifiers specialized to $\hsame$. The two required
$\hsame$-soundness premises are discharged by the identity proof on the given
component links. Thus the envelope classifier and the componentwise $\hsame$
classifier have exactly the same histories under the displayed
pair-representation coherence.
\end{proof}

This exactness statement instantiates the roadmap template as traditional
ordered-pair equality agreement over the BEDC source $\mathsf{BHist}$ with
$\Cont$, carrier $\mathsf{ProdHistoryCarrier}$, classifier agreement between
the envelope and componentwise $\hsame$ classifiers, stability by
$\mathsf{ProdPairRepCoherent}_{L,R,\hsame,\hsame}$, ledger through displayed
pair representations, and status $\mathsf{ProofTarget}$.

\begin{theorem}[Product componentwise history classifier displayed exactness]
\label{thm:prod-component-history-classifier-displayed-exactness}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be source-history carriers, let
$\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$ be their source
classifiers. Assume $\mathsf{ProdPairRepCoherent}_{L,R,\sim_L,\sim_R}$ and the
displayed source transitivity laws
$$
\forall a\,b\,c.\;a\sim_L b\to b\sim_L c\to a\sim_L c
\qquad\hbox{and}\qquad
\forall a\,b\,c.\;a\sim_R b\to b\sim_R c\to a\sim_R c.
$$
If
$\mathsf{ProdPairRep}_{L,R}(h,l,r)$ and
$\mathsf{ProdPairRep}_{L,R}(k,l',r')$, then
$$
\mathsf{ProdComponentHistoryClassifier}_{L,R,\sim_L,\sim_R}(h,k)
\Longleftrightarrow
(l\sim_L l')\wedge(r\sim_R r').
$$
\end{theorem}
\begin{proof}
For the forward direction, apply
Theorem~\ref{thm:prod-component-history-classifier-inversion} to the two
displayed pair representations and the assumed componentwise classifier. For
the reverse direction, use the displayed pair representations
$\mathsf{ProdPairRep}_{L,R}(h,l,r)$ and
$\mathsf{ProdPairRep}_{L,R}(k,l',r')$ as the existential witnesses in
Definition~\ref{def:prod-component-history-classifier}; the two displayed
component relations supply the remaining conjuncts.
\end{proof}

\begin{definition}[Prod stability certificate]
\label{def:prod-stability-certificate}
The checked stability subcertificate consists of:
\begin{enumerate}
  \item componentwise reflexivity obtained from the two source reflexivity fields
  \item componentwise transitivity obtained from the two source transitivity fields
  \item coordinate exposure: any
  $\mathsf{ProdClassifierSpec}(R_A,R_B,x,y)$ witness yields
  $R_A(x.1,y.1)$ and $R_B(x.2,y.2)$
\end{enumerate}
Relation-level symmetry is supplied by
Theorem~\ref{thm:prod-classifier-symm-from-source-symmetry}; the
source-certificate theorem is obtained from the two $\mathsf{equiv\_symm}$
fields, while the $\hsame$ specialization is
Theorem~\ref{thm:prod-classifier-hsame-symm}.
\end{definition}
\leanchecked{BEDC.Derived.ProdUp.prod\_stability\_certificate\_fields}

\begin{theorem}[Product classifier transitivity at the typed level]
\label{thm:prod-classifier-transitivity}
Let $R_A : A \to A \to \mathsf{Prop}$ and
$R_B : B \to B \to \mathsf{Prop}$ be source classifier relations.  If both
$R_A$ and $R_B$ are transitive, then for product carriers $x$, $y$, and $z$,
$$
  \mathsf{ProdClassifierSpec}(R_A,R_B,x,y)
  \quad\text{and}\quad
  \mathsf{ProdClassifierSpec}(R_A,R_B,y,z)
$$
imply $\mathsf{ProdClassifierSpec}(R_A,R_B,x,z)$.
\end{theorem}
\leanchecked{BEDC.Derived.ProdUp.ProdClassifierSpec\_trans}
\begin{proof}
Invert the product classifier witnesses by their constructor. The first
components compose by transitivity of $R_A$, the second components compose by
transitivity of $R_B$, and the paired typed witness rebuilds the product
classifier.
\end{proof}

\begin{theorem}[Product classifier symmetry from source symmetry]
\label{thm:prod-classifier-symm-from-source-symmetry}
Let $R_A : A \to A \to \mathsf{Prop}$ and
$R_B : B \to B \to \mathsf{Prop}$ be source classifier relations. If
$$
\forall a\,a'.\; R_A(a,a')\to R_A(a',a)
$$
and
$$
\forall b\,b'.\; R_B(b,b')\to R_B(b',b)
$$
hold, then for product carriers $x$ and $y$,
$\mathsf{ProdClassifierSpec}(R_A,R_B,x,y)$ implies
$\mathsf{ProdClassifierSpec}(R_A,R_B,y,x)$.
\end{theorem}
\begin{proof}
Invert the product classifier witness into its two coordinate witnesses.
Apply source symmetry for $R_A$ to the first coordinate and source symmetry for
$R_B$ to the second coordinate, then rebuild the product classifier with the
same constructor in the opposite order.
\end{proof}

\begin{theorem}[Product classifier symmetry from source certificates]
\label{thm:prod-classifier-symm-from-namecert}
Let $L,R:\mathsf{BHist}\to\mathsf{Prop}$ be BEDC history carriers, let
$\sim_L,\sim_R:\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$ be their
source classifiers, and let
$\mathsf{cert}_L:\NameCert(L,\sim_L)$ and
$\mathsf{cert}_R:\NameCert(R,\sim_R)$ be source name certificates. For product
carriers $x,y:\mathsf{ProdCarrier}(\mathsf{BHist},\mathsf{BHist})$,
$\mathsf{ProdClassifierSpec}(\sim_L,\sim_R,x,y)$ implies
$\mathsf{ProdClassifierSpec}(\sim_L,\sim_R,y,x)$.
\end{theorem}
\begin{proof}
Invert the product classifier witness into its left and right component
classifier proofs. Apply the $\mathsf{equiv\_symm}$ field of
$\mathsf{cert}_L$ to reverse the left component, and the
$\mathsf{equiv\_symm}$ field of $\mathsf{cert}_R$ to reverse the right
component. The product classifier constructor then rebuilds the componentwise
witness in the opposite order.
\end{proof}

\begin{theorem}[History product classifier is symmetric]
\label{thm:prod-classifier-hsame-symm}
For pairs of finite-kernel histories, if the product classifier relates \(x\) to \(y\) componentwise by \(\hsame\), then it relates \(y\) to \(x\).
\end{theorem}
\begin{proof}
Invert the componentwise product classifier. Each component witness reverses by symmetry of \(\hsame\), and the reversed witnesses rebuild the product classifier in the opposite direction.
\end{proof}
\leanchecked{BEDC.Derived.ProdUp.ProdClassifierSpec\_hsame\_symm}

\input{parts/concrete_instances/09_prod_ledger_and_semantic_certificate.tex}
