\chapter{A Concrete Naming Certificate for $\RiemannStieltjesUp$}
\label{ch:concrete-instances-riemannstieltjes-namecert}
\origin{human}

Following Riemann and Stieltjes, the $\RiemannStieltjesUp$ packet records a finite tagged-sum integration surface in which a regulated integrand is read against a bounded-variation integrator. It sits over the variation ledger of \autoref{ch:concrete-instances-boundedvariation-namecert}, the regulated-integral handoff of \autoref{ch:concrete-instances-regulatedintegral-namecert}, the finite tagged-sum surface of \autoref{ch:concrete-instances-riemannsum-namecert}, and the dyadic step approximation rows of \autoref{ch:concrete-instances-dyadicstepfunction-namecert}. The packet names only the displayed finite rows needed for a constructive Riemann--Stieltjes read; it does not introduce a measure space, a completed integrator, a host function quotient, or an ambient choice principle.

\begin{definition}[Riemann--Stieltjes carrier]
\label{def:riemann-stieltjes-carrier}
A $\RiemannStieltjesUp$ carrier is a finite $\BHist$ packet
$$
R=(F,A,T,S,I,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the regulated integrand row, exposing only the finitely requested approximation windows and endpoint reads.
\item $A$ is the bounded-variation integrator row, carrying the displayed partition-variation ledger and transported endpoint jumps.
\item $T$ is the tagged partition and $\RiemannSumUp$ row, with each tag contained in its displayed interval cell.
\item $S$ is the $\DyadicStepFunctionUp$ approximation row used to replace the regulated integrand on the displayed refinement.
\item $I$ is the $\RegulatedIntegralUp$ handoff row reached after the step approximation, variation ledger, and tagged-sum rows are present.
\item $E$ is the $\RealUp$ endpoint seal for the final accepted integral read.
\item $H$ records componentwise $\hsame$ transport for the integrand, integrator, partition, step approximation, handoff, endpoint seal, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from partition cells to tag reads, from tag reads to step approximants, from variation jumps to finite sums, and from the handoff row to the $\RealUp$ seal.
\item $P$ is the $\Pkg$ provenance over $\RiemannStieltjesUp$, $\RegulatedIntegralUp$, $\BoundedVariationUp$, $\RiemannSumUp$, $\DyadicStepFunctionUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RiemannStieltjesUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,A,T,S,I,E,H,C,P,N$. It has no coordinate for Lebesgue integration, measure completion, selected limits, host real equality, a quotient of integrands or integrators, or a standard bridge.
\end{definition}

\begin{theorem}[Riemann--Stieltjes NameCert obligations]
\label{thm:riemann-stieltjes-namecert-obligations}
For an accepted $\RiemannStieltjesUp$ carrier $R=(F,A,T,S,I,E,H,C,P,N)$, the local $\NameCert_{\RiemannStieltjesUp}$ surface consists of exactly five rows:
\begin{enumerate}
\item carrier admission for the displayed tuple $F,A,T,S,I,E,H,C,P,N$;
\item partition-refinement stability for the tagged $\RiemannSumUp$ row $T$ and dyadic step row $S$;
\item bounded-variation ledger control for the integrator row $A$ and its transported endpoint jumps;
\item regulated-integral handoff through $I$ after the finite sum and variation rows have been displayed;
\item no-escape from host measure data, completion data, choice data, hidden function quotients, and ambient real equality.
\end{enumerate}
These rows are read through the finite route
$$
F,A\longmapsto T\longmapsto S\longmapsto I\longmapsto E
$$
together with $H,C,P,N$.
\end{theorem}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesUpTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is the projection of \autoref{def:riemann-stieltjes-carrier}. The rows $F$ and $A$ expose the regulated integrand and bounded-variation integrator before any tagged sum is accepted.

Partition-refinement stability is checked on the displayed row $T$. A common refinement transports tags and cell containment through the visible $\hsame$ rows, and the dyadic step row $S$ reads the same refined cells without adding a host-level function comparison.

Bounded-variation ledger control is supplied by $A$. The integrator contributes only transported endpoint jumps and finite variation ledgers, so every summand is controlled by displayed bounded-variation data rather than by a measure or completed variation object.

The handoff row $I$ is downstream of $T$ and $S$. Continuation replay through $C$ rebuilds the same path, while $P$ and $N$ record provenance and local naming. Since the excluded host objects do not occur among the carrier coordinates, the listed five rows exhaust the certificate obligations.
\end{proof}

\begin{theorem}[Riemann--Stieltjes regulated-integral handoff]
\label{thm:riemann-stieltjes-regulated-integral-handoff}
Every accepted $\RiemannStieltjesUp$ sum read factors through the displayed dyadic-step and regulated-integral rows before reaching the $\RealUp$ seal. Concretely, a consumer of the endpoint row $E$ must first read the regulated integrand row $F$, the bounded-variation integrator row $A$, the tagged sum row $T$, the dyadic step approximation row $S$, and the regulated-integral handoff row $I$.
\end{theorem}
\begin{proof}
Project an accepted carrier as $R=(F,A,T,S,I,E,H,C,P,N)$. The rows $F$ and $A$ supply the only integrand and integrator data available to the packet, and $T$ records the finite tagged partition on which those data are read.

The row $S$ is the dyadic step approximation surface attached to that displayed partition. Thus a downstream read cannot pass directly from tags to a real endpoint seal; it must first consume the step row that makes the regulated integrand finite on the refinement.

The row $I$ then packages the regulated-integral handoff from the step approximation and bounded-variation ledger. Only after this handoff is displayed does $E$ expose a $\RealUp$ endpoint seal. Componentwise transport through $H$ and replay through $C$ preserve this order, and the package and local naming rows add no bypass coordinate.
\end{proof}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesCarrier\_regulated\_integral\_handoff}

\begin{theorem}[Riemann--Stieltjes Darboux mesh refinement]
\label{thm:riemann-stieltjes-darboux-mesh-refinement}
Every accepted $\RiemannStieltjesUp$ carrier refines a finite Darboux mesh through the displayed $\RegulatedIntegralUp$, $\BoundedVariationUp$, $\RiemannSumUp$, $\DyadicStepFunctionUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. For a carrier
$$
R=(F,A,T,S,I,E,H,C,P,N),
$$
any downstream Darboux or tagged-sum consumer must read the refined mesh from $T$ and $S$, the integrator control from $A$, the regulated-integral handoff from $I$, and the endpoint seal from $E$. The packet exports no selected limit, quotient of tagged sums, host integrand quotient, host integrator quotient, or ambient real equality beyond those displayed rows.
\end{theorem}
\begin{proof}
Project the accepted carrier as $R=(F,A,T,S,I,E,H,C,P,N)$. The only partition data available to the consumer is the finite tagged-sum row $T$, and the only step approximation data available on a refinement is the dyadic step row $S$.

Refine the displayed mesh by replaying the continuation row $C$. Each cell containment, tag read, and dyadic step replacement is transported componentwise through $H$, so the refinement is a BEDC row calculation rather than a host-level limit selection.

The bounded-variation row $A$ controls the integrator contribution on the refined cells. Its endpoint jumps and variation ledger are finite rows, and the regulated-integral handoff row $I$ can be read only after $A,T,S$ have all been displayed.

Finally, $P$ and $N$ route the refined mesh through the local package and classifier. Since equality is mediated only by $H$ and by the local $\NameCert_{\RiemannStieltjesUp}$ comparison, no quotient of tagged sums, selected limit, or ambient real equality is exported by the carrier.
\end{proof}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesCarrier\_darboux\_mesh\_refinement}

\begin{theorem}[Riemann--Stieltjes bounded-variation jump boundary]
\label{thm:riemann-stieltjes-bounded-variation-jump-boundary}
Every accepted $\RiemannStieltjesUp$ carrier reads integrator jump data only through the displayed $\BoundedVariationUp$ row before the tagged-sum and regulated-integral rows are consumed. For
$$
R=(F,A,T,S,I,E,H,C,P,N),
$$
the order of every jump-facing read is
$$
A \longrightarrow T,S \longrightarrow I \longrightarrow E .
$$
The route cannot replace bounded-variation evidence by a measure space, selected limit, host function quotient, or ambient choice.
\end{theorem}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesCarrier\_bounded\_variation\_jump\_boundary}
\begin{proof}
Project the carrier rows $F,A,T,S,I,E,H,C,P,N$ from \autoref{def:riemann-stieltjes-carrier}. The integrator row $A$ is the only displayed source of bounded-variation evidence and transported endpoint jumps.

Use \autoref{thm:riemann-stieltjes-namecert-obligations}. It places bounded-variation ledger control before the regulated-integral handoff, so a tagged-sum read cannot consume jump data except through $A$.

Apply \autoref{thm:riemann-stieltjes-darboux-mesh-refinement}. The finite mesh and dyadic step rows $T,S$ are read after the bounded-variation row and before the handoff row $I$, and the endpoint seal $E$ remains downstream of that handoff.

The structural rows $H,C,P,N$ transport, replay, source, and name the same order. Since the packet has no coordinate for measure spaces, selected limits, host function quotients, or ambient choice, the displayed bounded-variation jump boundary cannot be replaced by any of them.
\end{proof}

\begin{theorem}[Riemann--Stieltjes refinement-window exhaustion]
\label{thm:riemann-stieltjes-refinement-window-exhaustion}
For every accepted $\RiemannStieltjesUp$ carrier
$$
R=(F,A,T,S,I,E,H,C,P,N),
$$
every downstream refinement-window read is exhausted by the displayed rows $A,T,S,I,E,H,C,P,N$. In particular, no consumer can bypass the $\RiemannSumUp$ row $T$, the $\DyadicStepFunctionUp$ row $S$, the $\BoundedVariationUp$ row $A$, the $\RegulatedIntegralUp$ row $I$, or the $\RealUp$ seal $E$ when reading a refinement of the Riemann--Stieltjes packet.
\end{theorem}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesCarrier\_refinement\_window\_exhaustion}
\begin{proof}
Project the accepted carrier from \autoref{def:riemann-stieltjes-carrier}. The only refinement-facing rows available to a consumer are the bounded-variation integrator row $A$, the tagged-sum row $T$, the dyadic step row $S$, the regulated-integral handoff row $I$, the endpoint seal $E$, and the structural rows $H,C,P,N$.

Apply \autoref{thm:riemann-stieltjes-regulated-integral-handoff}. It forces every endpoint-facing read to pass through $F,A,T,S,I$ before $E$ is visible, so the endpoint seal cannot be used as a shortcut around the displayed finite rows.

Apply \autoref{thm:riemann-stieltjes-darboux-mesh-refinement} and \autoref{thm:riemann-stieltjes-bounded-variation-jump-boundary}. The former confines mesh refinement to the tagged-sum and dyadic-step route, while the latter places every jump-facing integrator read behind the bounded-variation row $A$.

The rows $H,C,P,N$ transport, replay, source, and name exactly this route. Since the carrier has no coordinate for a hidden refinement oracle, measure completion, selected limiting partition, host function quotient, or ambient real equality, the listed rows exhaust every downstream refinement-window read.
\end{proof}

\begin{theorem}[Riemann--Stieltjes regulated-integrator transport]
\label{thm:riemann-stieltjes-regulated-integrator-transport}
Every $\RiemannStieltjesUp$ read that is consumed as a regulated-integral handoff must pass through the bounded-variation integrator row $A$ and the tagged-sum row $T$ before the handoff row $I$ is visible. For an accepted carrier
$$
R=(F,A,T,S,I,E,H,C,P,N),
$$
the route to $I$ is the displayed BEDC row route
$$
F,A,T,S,H,C,P,N \longrightarrow I .
$$
It cannot be replaced by a host measure integral, a quotient of integrators, a selected limiting partition, or an unrecorded real equality.
\end{theorem}
\leanchecked{BEDC.Derived.RiemannStieltjesUp.RiemannStieltjesCarrier\_regulated\_integrator\_transport}
\begin{proof}
Project the carrier from \autoref{def:riemann-stieltjes-carrier}. The regulated integrand row $F$ and the bounded-variation integrator row $A$ are the only sources from which the packet can read the two integration inputs.

Use the tagged-sum and step rows next. The row $T$ displays the finite tagged partition, while $S$ records the dyadic step approximation used by the regulated-integral handoff.

The handoff row $I$ is therefore downstream of $F,A,T,S$. Componentwise transport through $H$ and continuation replay through $C$ preserve the same order, and $P,N$ record provenance and local naming without adding any bypass coordinate.

Since the carrier has no coordinate for measure integration, integrator quotients, selected limiting partitions, or host real equality, every regulated-integrator transport consumed by the packet remains on this finite route.
\end{proof}

\begin{theorem}[Riemann--Stieltjes bounded-variation ledger]
\label{thm:riemann-stieltjes-bounded-variation-ledger}
For every accepted $\RiemannStieltjesUp$ carrier $R=(F,A,T,S,I,E,H,C,P,N)$, each integrator jump, variation read, and endpoint contribution used by the tagged sum is consumed as a visible $\BHist$ ledger row inside $A$ before it is transported through $H,C,P,N$. The packet exports no hidden variation functional, measure-space control object, selected jump enumeration, or quotient of integrators.
\end{theorem}
\begin{proof}
Read the bounded-variation component $A$ from the carrier. By \autoref{thm:riemann-stieltjes-bounded-variation-jump-boundary}, jump-facing reads begin at $A$ and cannot enter the tagged-sum route from any outside source.

The finite tagged-sum row $T$ consumes only the displayed cells and tags, while the dyadic step row $S$ supplies the corresponding finite integrand approximants. Thus every variation contribution used in the sum is already a visible row before the handoff row $I$ is read.

Transport and replay do not create new variation data. The rows $H$ and $C$ move and replay the same ledger entries, while $P$ and $N$ identify the package and local NameCert surface. The excluded host objects have no coordinate in $R$, so the ledger is exactly the displayed bounded-variation row.
\end{proof}

\begin{theorem}[Riemann--Stieltjes mesh refinement stability]
\label{thm:riemann-stieltjes-mesh-refinement-stability}
If an accepted $\RiemannStieltjesUp$ carrier is read along a mesh refinement, the refined packet preserves the same componentwise $\hsame$ transport, displayed $\Cont$ replay, and $\Pkg$ provenance route over $F,A,T,S,I,E,H,C,P,N$. Refinement may subdivide the visible tagged partition row, but it cannot introduce a new integrator, a new regulated-integral handoff, host function equality, selected limits, or a measure-space bridge.
\end{theorem}
\begin{proof}
Start with the Darboux mesh-refinement theorem, \autoref{thm:riemann-stieltjes-darboux-mesh-refinement}. It confines every refinement-facing read to the displayed rows $T,S,A,I,E$ together with the structural rows.

Refining the mesh changes only the visible tagged partition and the corresponding dyadic step rows. The bounded-variation ledger remains the row $A$, and the regulated-integral handoff remains the row $I$ reached after the refined finite data are displayed.

The structural route is unchanged. Componentwise $\hsame$ transport is recorded by $H$, continuation replay by $C$, and provenance by $P$ before the local naming row $N$ accepts the refined packet. Because no host equality, selected limit, new integrator, or measure bridge occurs among the coordinates, refinement preserves the same finite BEDC route.
\end{proof}

\begin{theorem}[Riemann--Stieltjes bounded-variation partition coverage]
\label{thm:riemann-stieltjes-bounded-variation-partition-coverage}
For every accepted $\RiemannStieltjesUp$ carrier
$$
R=(F,A,T,S,I,E,H,C,P,N),
$$
each cell of the finite $\BHist$ partition row $T$ is covered by a bounded-variation jump or oscillation row displayed inside $A$ before the regulated-integral handoff $I$ is public. The coverage is stable under componentwise $\hsame$ transport, replayed by $\Cont$ through $C$, sourced by the $\Pkg$ provenance row $P$, and named by the local $\NameCert_{\RiemannStieltjesUp}$ row $N$.
\end{theorem}
\begin{proof}
Project the carrier and read the finite partition row $T$. Its cells and tags are $\BHist$ entries, so coverage can be checked cell by cell rather than by a host partition object.

Induct over the displayed partition refinement rows. The base row is the original tagged partition, where \autoref{thm:riemann-stieltjes-bounded-variation-ledger} supplies the integrator jump and variation entries from $A$. In the refinement step, the subdivided cells inherit the same bounded-variation control by the mesh-refinement stability theorem and the bounded-variation jump boundary.

The structural rows preserve the coverage. Transport through $H$ moves the displayed jump and oscillation rows componentwise, replay through $C$ keeps the cell-to-jump route in the same order, and $P,N$ record the package source and local certificate name. Thus $I$ can only read a partition whose cells are already covered by the displayed bounded-variation rows.
\end{proof}

\begin{theorem}[Riemann--Stieltjes regulated-integral mesh handoff]
\label{thm:riemann-stieltjes-regulated-integral-mesh-handoff}
Every mesh-facing read of an accepted $\RiemannStieltjesUp$ carrier reaches the $\RegulatedIntegralUp$ handoff row $I$ only after the finite $\BHist$ partition row $T$, the bounded-variation jump and oscillation rows in $A$, and the dyadic step approximation row $S$ have been displayed. The route is invariant under $\hsame$ transport, replayed by $\Cont$, sourced by $\Pkg$ provenance, and accepted by the local $\NameCert$ row.
\end{theorem}
\begin{proof}
Project $R=(F,A,T,S,I,E,H,C,P,N)$. The endpoint seal $E$ is downstream of $I$, and the handoff theorem already places $I$ after the integrand, integrator, tagged-sum, and dyadic-step rows.

Induct over the finite mesh refinement rows. At the base mesh, the partition row $T$ and step row $S$ are displayed directly, and the bounded-variation partition coverage theorem supplies the jump and oscillation rows from $A$. At a refinement step, \autoref{thm:riemann-stieltjes-mesh-refinement-stability} preserves the same $A,T,S,I$ order while subdividing only the visible partition row.

Finally transport and replay do not change the route. The row $H$ moves each displayed mesh, jump, oscillation, and step entry componentwise; $C$ replays the handoff order; and $P,N$ provide provenance and local naming. Hence a regulated-integral consumer cannot reach $I$ without first reading the displayed finite mesh and bounded-variation control.
\end{proof}

\begin{theorem}[Riemann--Stieltjes step-integrator exactness]
\label{thm:riemann-stieltjes-step-integrator-exactness}
For an accepted $\RiemannStieltjesUp$ carrier $R=(F,A,T,S,I,E,H,C,P,N)$, each dyadic step contribution consumed by the handoff row $I$ is exact with respect to the bounded-variation integrator row $A$: the value is computed from the displayed step value in $S$, the corresponding finite $\BHist$ partition cell in $T$, and the jump or oscillation ledger row in $A$. No hidden measure integral, selected limiting partition, host integrator quotient, or ambient real equality is used.
\end{theorem}
\begin{proof}
Read the step row $S$ together with the partition row $T$. Each step contribution names a displayed cell and a displayed step value, so the integrator contribution must be supplied by the bounded-variation ledger already present in $A$.

Proceed by induction over the displayed partition refinement rows. The base contribution is exact by direct projection from $S,T,A$: the step value is paired with the integrator jump or oscillation entry carried by the same cell. In the refinement step, the mesh-refinement stability theorem transports the subdivided step entries, while bounded-variation partition coverage supplies the matching integrator rows for every child cell.

The remaining structural rows only preserve this calculation. Componentwise $\hsame$ transport in $H$ keeps step values, cells, and integrator ledger rows aligned; $\Cont$ replay through $C$ repeats the same finite route; and $P,N$ record provenance and local NameCert acceptance. The excluded host objects are absent from the carrier, so step-integrator exactness is a finite BEDC row calculation.
\end{proof}

\closureat{RiemannStieltjesUp}{seedStr}

\begin{closurestatus}{\RiemannStieltjesUp}
  \constructivestory{A $\RiemannStieltjesUp$ packet is generated from a regulated integrand row, bounded-variation integrator row, tagged partition and Riemann-sum row, dyadic step approximation row, regulated-integral handoff row, Real endpoint seal, componentwise transport, continuation replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riemann-stieltjes-carrier}, \autoref{thm:riemann-stieltjes-namecert-obligations}, and \autoref{thm:riemann-stieltjes-regulated-integral-handoff} seed the finite Riemann--Stieltjes boundary over $\RegulatedIntegralUp$, $\BoundedVariationUp$, $\RiemannSumUp$, $\DyadicStepFunctionUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lebesgue integration, measure completion, selected limits, host real equality, any quotient of integrands or integrators, Lean verification, or any standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, partition-refinement stability, bounded-variation ledger control, regulated-integral handoff, transport, replay, provenance, and no-escape for BEDC.Derived.RiemannStieltjesUp.}
\end{closurestatus}
