\chapter{A Concrete Naming Certificate for $\LocatednessModulusUp$}
\label{ch:concrete-instances-locatedness-modulus-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\LocatednessModulusUp$ packet names the finite budget by which a positive rational tolerance request is turned into displayed interval and real-name window data. It sits between the endpoint surface of \autoref{ch:concrete-instances-locatedinterval-namecert}, the rational-cell ledger of \autoref{ch:concrete-instances-rationalinterval-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation gateway of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet records an explicit locatedness service for constructive Real completion; it is not a host trichotomy, quotient real equality, selected endpoint functional, or ambient completeness theorem.

\begin{definition}[Locatedness modulus carrier]
\label{def:locatedness-modulus-carrier}
A $\LocatednessModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(q,L,I,D,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $q$ is the positive rational tolerance request supplied to the locatedness service.
\item $L$ is the $\LocatedIntervalUp$ endpoint surface whose lower and upper endpoint rows are inspected under that request.
\item $I$ is the finite $\RationalIntervalUp$ cell ledger that records the rational windows admitted for the requested tolerance.
\item $D$ is the $\DyadicRatCoreUp$ or dyadic-interval refinement ledger that records the dyadic rows used to tighten the rational cells.
\item $S$ is the $\StreamNameUp$ finite-window row used to inspect the endpoint names and the real-name route at precision $q$.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the inspected stream window.
\item $E$ is the $\RealUp$ seal row reached after the readback and refinement budget have been displayed.
\item $H$ records componentwise $\hsame$ transport for the tolerance request, located interval, rational cells, dyadic refinements, stream windows, readbacks, real-seal rows, continuation routes, provenance rows, and local naming row.
\item $C$ records the displayed $\Cont$ replay from the tolerance request through the located interval, rational cells, dyadic refinement ledger, stream window, regular readback, and real-name seal.
\item $P$ is the $\Pkg$ provenance over $\LocatedIntervalUp$, $\RationalIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatednessModulusUp}$ row.
\end{enumerate}
The carrier predicate is exactly the assertion that these rows form one finite locatedness-budget packet. It has no coordinate for a host order trichotomy, quotient real equality, selected endpoints, a global apartness oracle, or ambient Real completeness.
\end{definition}

\begin{theorem}[Locatedness modulus NameCert obligations]
\label{thm:locatedness-modulus-namecert-obligations}
For every accepted $\LocatednessModulusUp$ carrier $M=(q,L,I,D,S,R,E,H,C,P,N)$, the local $\NameCert_{\LocatednessModulusUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission, requiring the displayed tolerance request, located interval, rational-cell ledger, dyadic refinement rows, stream windows, regular readbacks, real-seal rows, transport, continuation, provenance, and local naming data to inhabit one $\BHist$ packet;
\item tolerance-cell compatibility, requiring every rational cell in $I$ to be admitted for the request $q$ and for the endpoint surface $L$;
\item dyadic refinement stability, requiring every dyadic row in $D$ to refine a displayed rational cell rather than replace it by a host endpoint choice;
\item window transport, requiring $S,R,E,H,C$ to preserve the same tolerance request through finite endpoint windows and real-seal readbacks;
\item non-escape, excluding host trichotomy, quotient real equality, selected endpoints, global apartness choice, and ambient completeness from the exported certificate.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\leanchecked{BEDC.Derived.LocatednessModulusUp.TasteGate.LocatednessModulusTasteGate\_single\_carrier\_alignment}
\leanchecked{BEDC.Derived.LocatednessModulusUp.LocatednessModulusTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier of \autoref{def:locatedness-modulus-carrier}. The projection exposes exactly the tolerance request, located interval, rational cells, dyadic refinements, stream windows, readbacks, real-seal row, and structural rows $H,C,P,N$.

Carrier admission is the finite tuple $M$ itself. Tolerance-cell compatibility is the assertion that the rational cells in $I$ are displayed as the cells admitted for $q$ and for the endpoint surface $L$.

Dyadic refinement stability reads the rows of $D$ only through the rational cells in $I$. Thus a dyadic refinement tightens the displayed finite budget and cannot introduce a selected host endpoint.

Window transport is supplied by $S,R,E,H,C$. The stream window, regular readback, and real-seal replay preserve the same request route through componentwise transport.

The exclusions follow from the carrier inventory. Since $M$ contains no coordinate for host trichotomy, quotient real equality, selected endpoints, a global apartness choice, or Real completeness, none can be exported by the local certificate.
\end{proof}

\begin{theorem}[Locatedness modulus window transport]
\label{thm:locatedness-modulus-window-transport}
Every finite consumer of an accepted $\LocatednessModulusUp$ carrier transports the tolerance request and endpoint windows through the route
$$
q \longmapsto L \longmapsto I,D \longmapsto S,R \longmapsto E \longmapsto H,C,P,N .
$$
Consequently a $\LocatedIntervalUp$, $\RegSeqRatUp$, or $\RealUp$ consumer receives the same requested tolerance together with its finite endpoint-window route, not a new host comparison of completed real values.
\end{theorem}
\leanchecked{BEDC.Derived.LocatednessModulusUp.LocatednessModulusCarrier\_window\_transport}
\begin{proof}
Start with an accepted carrier $M=(q,L,I,D,S,R,E,H,C,P,N)$. The only tolerance coordinate is $q$, and the only interval coordinate attached to it is the displayed $\LocatedIntervalUp$ surface $L$.

The rational cells $I$ and dyadic refinements $D$ are then read as the finite response to that request. Their transport keeps each cell and refinement attached to $q$ and $L$ because no other request or interval row is present.

The stream window $S$ and regular readback $R$ inspect the endpoint data through that same route. The real-seal row $E$ is reached only after those finite observations have been displayed.

Finally $H,C,P,N$ package the transport. Componentwise $\hsame$, continuation replay, provenance, and local naming keep the consumer inside the requested finite budget, so no host comparison of completed real values can be inserted.
\end{proof}

\begin{theorem}[Locatedness modulus Real-seal non-escape]
\label{thm:locatedness-modulus-real-seal-non-escape}
For every accepted $\LocatednessModulusUp$ carrier $M=(q,L,I,D,S,R,E,H,C,P,N)$, every Real-facing read factors through the displayed tolerance request, located interval surface, rational-cell ledger, dyadic refinement rows, stream window, regular readback, real-seal row, transport row, continuation row, provenance row, and local naming row. It cannot export host trichotomy, quotient real equality, selected endpoints, a global apartness oracle, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.LocatednessModulusUp.LocatednessModulusCarrier\_real\_seal\_non\_escape}
\begin{proof}
Read the Real-facing part of \autoref{def:locatedness-modulus-carrier}. The only real-name boundary is the seal row $E$, and it is preceded by the finite window $S$, readback $R$, dyadic refinement ledger $D$, rational cells $I$, located interval surface $L$, and tolerance request $q$.

Transport does not add a second Real-facing source. The componentwise rows $H$ and displayed replay $C$ move the same listed data through the same packet, while $P$ and $N$ record the package and local certificate provenance.

It remains to rule out non-displayed Real data. The carrier has no field for host trichotomy, quotient real equality, selected endpoints, a global apartness oracle, or ambient completeness; every Real-facing read is therefore a projection from $M$.
\end{proof}
\leanchecked{BEDC.Derived.LocatednessModulusUp.LocatednessModulusRealSeal\_nonescape}

\closureat{LocatednessModulusUp}{seedStr}

\begin{closurestatus}{\LocatednessModulusUp}
  \constructivestory{A $\LocatednessModulusUp$ packet is generated from a rational tolerance request, a $\LocatedIntervalUp$ endpoint surface, $\RationalIntervalUp$ cells, $\DyadicRatCoreUp$ refinement rows, $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, a $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:locatedness-modulus-carrier}, \autoref{thm:locatedness-modulus-namecert-obligations}, \autoref{thm:locatedness-modulus-window-transport}, and \autoref{thm:locatedness-modulus-real-seal-non-escape} seed the finite locatedness-budget surface for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host trichotomy, quotient real equality, selected endpoints, global apartness choice, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires carrier admission, tolerance-window transport, dyadic refinement stability, locatedness decision budget, and Real-seal non-escape proofs for BEDC.Derived.LocatednessModulusUp.}
\end{closurestatus}
