\chapter{A Concrete Naming Certificate for $\RealMetricUp$}
\label{ch:concrete-instances-real-metric-namecert}
\origin{human}

Following Bishop and Bridges, the $\RealMetricUp$ packet names the standard metric on displayed regular real names by routing distance through finite absolute-value, stream-window, regular-rational, and dyadic-tolerance rows. It sits between the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the absolute-value surface of \autoref{ch:concrete-instances-real-abs-namecert}, the generic metric obligations of \autoref{ch:concrete-instances-metric-namecert}, the stream and regular-Cauchy readback interfaces of \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The chapter records the finite NameCert boundary for real distance; it does not identify quotient reals, select limits, invoke trichotomy, or assert completeness.

\begin{definition}[Real metric carrier]
\label{def:real-metric-carrier}
A $\RealMetricUp$ carrier is a finite $\BHist$ packet
$$
M_{\Real}=(X,Y,A,D,S,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two displayed $\RealUp$ seals whose distance is being named.
\item $A$ is the $\RealAbsUp$ distance row for the displayed difference read from $X$ and $Y$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used to present finite distance requests and triangle budgets.
\item $S$ is the finite $\StreamNameUp$ window family opened from the two real-name seals before the distance row is read.
\item $R$ is the $\RegSeqRatUp$ regular-rational readback row attached to the displayed stream windows and dyadic tolerances.
\item $H$ records componentwise $\hsame$ transport for the two real seals, absolute-value distance row, dyadic tolerance row, stream windows, regular readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a distance request through $X,Y$, then through $S,R,D$, into the $\RealAbsUp$ row $A$, and finally into the generic $\MetricUp$ laws consumed downstream.
\item $P$ is the $\Pkg$ provenance over $\RealMetricUp$, $\RealUp$, $\RealAbsUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,A,D,S,R,H,C,P,N$. The carrier has no coordinate for host real equality, quotient real representatives, selected limits, trichotomy, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Real metric NameCert obligations]
\label{thm:real-metric-namecert-obligations}
For every accepted $\RealMetricUp$ carrier $M_{\Real}=(X,Y,A,D,S,R,H,C,P,N)$, the local $\NameCert_{\RealMetricUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the displayed endpoint seals, absolute-value distance row, dyadic tolerance row, stream windows, regular readback, transport, replay, provenance, and local naming row;
\item distance-row exposure, requiring every public distance read to pass from the endpoint seals $X,Y$ through the finite windows $S$, the regular readback $R$, and the dyadic tolerance row $D$ before it reaches the $\RealAbsUp$ distance row $A$;
\item symmetry route, requiring the classifier for the reversed endpoint order to reuse the same $\RealAbsUp$ row after componentwise transport of the two endpoint seals and their readback rows;
\item zero-distance classifier handoff, requiring a zero-distance request to be handed to the displayed $\RealUp$ seal classifier through the same $S,R,D,A$ route rather than through host equality;
\item triangle-budget handoff, requiring any triangle use to present the two endpoint distance rows and the composed dyadic tolerance budget before reading the corresponding $\MetricUp$ triangle law;
\item refusal of host real equality, quotient reals, selected limits, trichotomy, and completeness as NameCert data.
\end{enumerate}
No NameCert obligation is stored outside these finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.RealMetricUp.RealMetricTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:real-metric-carrier}. The only available distance data are the endpoint seals $X,Y$, the absolute-value distance row $A$, the dyadic tolerance row $D$, the stream windows $S$, the regular readback $R$, and the structural rows $H,C,P,N$.

Distance-row exposure is forced by the displayed route. A public distance request first opens finite windows on the two real names, reads the corresponding regular rational data, records the dyadic tolerance request, and only then reaches the $\RealAbsUp$ row naming the absolute value of the displayed difference.

Symmetry and zero-distance reads use the same classifier surface. Reversing the endpoints transports $X$ and $Y$ componentwise through $H$ and replays the same windows and readback through $C$; a zero-distance request then returns to the displayed $\RealUp$ seal classifier through $S,R,D,A$ rather than by comparing host reals.

Triangle use is downstream of the same finite route. The generic $\MetricUp$ triangle law is readable only after the three endpoint pairs have exposed their $\RealAbsUp$ distance rows and after the dyadic tolerance budgets have been composed in $D$.

Finally, provenance is exhausted by $P$ and $N$. Since host real equality, quotient representatives, selected limits, trichotomy, and completeness are not coordinates of $M_{\Real}$, the local NameCert surface cannot export them.
\end{proof}

\begin{theorem}[Real metric absolute-value distance handoff]
\label{thm:real-metric-absolute-value-distance-handoff}
Every accepted $\RealMetricUp$ distance consumer factors through the $\RealAbsUp$ row for the displayed endpoint difference and through the $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ readback route before it may read any $\MetricUp$ law. In particular, symmetry, zero-distance, and triangle consumers receive only the displayed rows
$$
\RealUp,\RealAbsUp,\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp,\MetricUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
The packet exports no host real equality, quotient real representative, selected limit, trichotomy, or completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.RealMetricUp.RealMetricCarrier\_absolute\_value\_distance\_handoff}
\begin{proof}
Let a distance consumer read an accepted packet $M_{\Real}=(X,Y,A,D,S,R,H,C,P,N)$. Carrier admission gives the consumer access only to the displayed endpoint, distance, tolerance, window, readback, transport, replay, provenance, and local naming rows.

The distance value is therefore obtained through the absolute-value route. The endpoint seals $X,Y$ provide the displayed difference source, $S$ opens the finite windows, $R$ supplies regular rational readback, $D$ records the dyadic tolerance request, and $A$ names the resulting $\RealAbsUp$ distance row.

Only after that route is displayed may the consumer invoke a generic $\MetricUp$ law. Symmetry reuses $A$ under endpoint transport, zero-distance returns through the displayed $\RealUp$ seal classifier, and triangle reads the composed dyadic budget before applying the metric triangle row.

The remaining coordinates are structural support. The $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows transport, replay, source, and name the same route, with no row from which host real equality, quotient representatives, selected limits, trichotomy, or completeness can be read.
\end{proof}

\begin{closurestatus}{\RealMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-metric-carrier}, \autoref{thm:real-metric-namecert-obligations}, and \autoref{thm:real-metric-absolute-value-distance-handoff} seed the finite real-metric surface over displayed $\RealUp$, $\RealAbsUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, host real equality, quotient real representatives, selected limits, trichotomy, or completeness of $\RealUp$.}
  \upgradepath{Obligation closure requires formal carrier admission, distance-row exposure, symmetry, zero-distance classifier handoff, triangle-budget handoff, and non-escape proofs for the same finite packet.}
  \constructivestory{A $\RealMetricUp$ packet is generated from two displayed RealUp seals, a RealAbs distance row for their displayed difference, a DyadicRatCore tolerance ledger, StreamName windows, RegSeqRat readback, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
