\chapter{A Concrete Naming Certificate for $\CauchyContinuousExtensionUp$}
\label{ch:concrete-instances-cauchy-continuous-extension-namecert}
\origin{human}

Following Bishop and Bridges-style constructive analysis, the $\CauchyContinuousExtensionUp$ packet records the finite handoff by which a Cauchy-continuous map on regular rational source data is read through the displayed completion route before it reaches a completed real-facing extension. It consumes the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular completion universal surface of \autoref{ch:concrete-instances-regular-cauchy-completion-universal-namecert}, the extension and uniqueness interface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, and the uniformly continuous extension route of \autoref{ch:concrete-instances-uniform-continuous-extension-namecert}. The chapter names the Cauchy-continuous completion-extension boundary as finite BEDC data; it does not turn host completion, quotient representatives, or function equality into packet coordinates.

\begin{definition}[Cauchy-continuous extension carrier]
\label{def:cauchy-continuous-extension-carrier}
A $\CauchyContinuousExtensionUp$ carrier is a finite $\BHist$ packet
$$
E=(S,W,D,F,U,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source regular-Cauchy row, read through $\RegSeqRatUp$ data and the regular source discipline of $\RegularCauchyCompletionUniversalUp$;
\item $W$ is the finite $\StreamNameUp$ window schedule for source observations and comparison requests;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling Cauchy-continuous requests on those windows;
\item $F$ is the Cauchy-continuous map row, recording that matching source windows inside the tolerance ledger produce matching target completion reads;
\item $U$ is the completion-universal extension row, read through $\CompletionUniversalPropertyUp$ and aligned with the $\UniformContinuousExtensionUp$ handoff when a uniform-modulus row is present;
\item $L$ is the uniqueness ledger comparing two extension rows over the same regular source, finite windows, dyadic ledger, Cauchy-continuous map row, and completion-universal extension row;
\item $H$ records componentwise $\hsame$ transport for $S,W,D,F,U,L$;
\item $C$ records the displayed $\Cont$ replay route forcing every extension read through $S,W,D,F,U,L$ in that order;
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyCompletionUniversalUp$, $\CompletionUniversalPropertyUp$, $\UniformContinuousExtensionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and local $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CauchyContinuousExtensionUp}$ row.
\end{enumerate}
The carrier stores no host function equality, quotient completion, selected limit, countable-choice schedule, or ambient completeness coordinate.
\end{definition}

\begin{theorem}[CauchyContinuousExtension NameCert obligations]
\label{thm:cauchy-continuous-extension-namecert-obligations}
For the carrier of \autoref{def:cauchy-continuous-extension-carrier}, the local $\NameCert_{\CauchyContinuousExtensionUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $E=(S,W,D,F,U,L,H,C,P,N)$;
\item regular source handoff, requiring each extension request to read $S$ through the finite windows $W$ and tolerance ledger $D$ before any completion-facing row is available;
\item Cauchy-continuous map control, requiring the map row $F$ to transport source Cauchy closeness into the target completion request consumed by $U$;
\item extension and uniqueness control, requiring the completion-universal row $U$ and uniqueness ledger $L$ to compare candidate extensions only over the same displayed source, window, tolerance, and map rows;
\item ledger non-escape, stating that $H,C,P,N$ expose no host function equality, quotient completion, selected limit, countable choice, or ambient completeness principle.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the packet in \autoref{def:cauchy-continuous-extension-carrier}. Carrier admission is exactly the presence of the ten rows $S,W,D,F,U,L,H,C,P,N$ with a local naming row.

The source handoff reads the first three coordinates. The regular source $S$ is visible only through the finite StreamName windows $W$ and the dyadic tolerance ledger $D$, so a completion-facing request cannot bypass the regular rational source route.

The map and extension clauses then read $F$ and $U$. The Cauchy-continuous map row $F$ is the only route from source Cauchy closeness to a target completion request, and $U$ is the only row that repacks that request through the completion-universal extension surface.

Finally the comparison and non-escape clauses inspect $L,H,C,P,N$. The uniqueness ledger $L$ compares extensions over the same displayed coordinates, while $H$ and $C$ only transport and replay those coordinates. Since no excluded principle is a carrier coordinate, the five obligations exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.CauchyContinuousExtensionUp.TasteGate.CauchyContinuousExtensionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyContinuousExtension regular source handoff]
\label{thm:cauchy-continuous-extension-regular-source-handoff}
Let $E=(S,W,D,F,U,L,H,C,P,N)$ be an accepted $\CauchyContinuousExtensionUp$ carrier. Every extension read exported by $U$ factors through the regular-Cauchy source row $S$, the finite window schedule $W$, the dyadic tolerance ledger $D$, and the Cauchy-continuous map row $F$ before it reaches the completion-universal extension surface.
\end{theorem}
\begin{proof}
Start with the source coordinates. The rows $S,W,D$ record the only regular-Cauchy observations available to the packet, so every admitted source read is a finite-window and tolerance-ledger read.

Apply the map row next. The row $F$ consumes exactly those source reads and records the Cauchy-continuous target request; it is not accompanied by a separate host map or selected target limit.

The extension row $U$ is therefore reached only after the route $S,W,D,F$ has been replayed. The $\Cont$ row $C$ preserves this order, and the provenance row $P$ records the same sibling surfaces. Hence every exported extension factors through the regular source handoff before reading the completion-universal surface.
\end{proof}

\begin{theorem}[CauchyContinuousExtension uniqueness ledger]
\label{thm:cauchy-continuous-extension-uniqueness-ledger}
Let $E=(S,W,D,F,U,L,H,C,P,N)$ and $E'=(S,W,D,F,U',L',H',C',P,N')$ be accepted $\CauchyContinuousExtensionUp$ carriers over the same regular source, finite windows, dyadic ledger, Cauchy-continuous map row, and provenance. Any comparison of the exported extension rows is exhausted by the displayed uniqueness ledgers $L$ and $L'$ together with componentwise $\hsame$ transport over $S,W,D,F,U$ and $U'$. No host function equality, quotient completion, selected limit, countable choice, or ambient completeness row can contribute to the comparison.
\end{theorem}
\begin{proof}
Read the shared coordinates $S,W,D,F,P$. They fix the regular source, window schedule, dyadic tolerance ledger, Cauchy-continuous map row, and provenance for both packets.

The only extension-specific coordinates are $U,L,H,C,N$ and $U',L',H',C',N'$. The ledgers $L$ and $L'$ compare the two extension rows over the same shared source route, while $H,H'$ provide only componentwise $\hsame$ transport and $C,C'$ replay only the displayed coordinate order.

Because neither carrier contains host function equality, quotient completion, selected limits, countable-choice schedules, or ambient completeness witnesses, no external comparison principle is available. The uniqueness judgement is exactly the local ledger comparison over the displayed Cauchy-continuous extension route.
\end{proof}

\begin{closurestatus}{\CauchyContinuousExtensionUp}
  \constructivestory{A $\CauchyContinuousExtensionUp$ packet is generated from a regular-Cauchy source row, finite StreamName windows, a DyadicRatCore tolerance ledger, a Cauchy-continuous map row, a CompletionUniversalProperty extension row, a uniqueness hsame ledger, displayed transport and replay rows, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-continuous-extension-carrier}, \autoref{thm:cauchy-continuous-extension-namecert-obligations}, \autoref{thm:cauchy-continuous-extension-regular-source-handoff}, and \autoref{thm:cauchy-continuous-extension-uniqueness-ledger} seed the finite Cauchy-continuous extension route over the L10 Real and Completion spine.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CauchyContinuousExtensionUp.TasteGate.CauchyContinuousExtensionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host function equality, quotient completion, selected limits, countable choice, ambient completeness, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, regular-source handoff, Cauchy-continuous map control, completion-universal extension control, uniqueness-ledger exactness, and ledger non-escape for BEDC.Derived.CauchyContinuousExtensionUp.}
\end{closurestatus}
