\chapter{A Concrete Naming Certificate for $\ModulusContinuityUp$}
\label{ch:concrete-instances-moduluscontinuity-namecert}
\origin{human}

Following Bishop and Bridges on constructive continuity with explicit moduli, the $\ModulusContinuityUp$ packet names the function-specific route by which a tolerance request is converted into a finite source-window budget before a Real or Completion consumer reads the target seal. It sits between the graph surface of \autoref{ch:concrete-instances-continuousmap-namecert}, the tolerance-to-window discipline of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite source observations of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet records the local modulus-continuity boundary used by Real and Completion routes; it is not an open-cover compactness principle, a selected limit, a quotient stream equality, a host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Modulus-continuity carrier]
\label{def:modulus-continuity-carrier}
A $\ModulusContinuityUp$ carrier is a finite $\BHist$ packet
$$
M=(G,S,K,D,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the $\ContinuousMapUp$ graph row for the named function, including the displayed source and target endpoints that every consumer must inspect before reading continuity data.
\item $S$ is the source $\StreamNameUp$ finite-window row whose entries supply the domain-side observations governed by the modulus.
\item $K$ is the $\CauchyModulusUp$ tolerance-to-window row, sending each positive dyadic target tolerance to the displayed finite source window read through $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger containing the target tolerance, the source-window budget, and the dyadic comparison rows used by $K$.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the source and target windows inspected by the graph and modulus rows.
\item $R$ is the terminal $\RealUp$ target seal reached only after $G,S,K,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the graph, source window, modulus row, dyadic ledger, regular readback, Real target seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a target tolerance request through $D$, then through the modulus row $K$, into the source window $S$, across the graph row $G$, through readback $Q$, and finally into the Real target seal $R$.
\item $P$ is the $\Pkg$ provenance over $\ModulusContinuityUp$, $\ContinuousMapUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ModulusContinuityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $G,S,K,D,Q,R,H,C,P,N$. It has no coordinate for open-cover compactness, selected limits, quotient stream equality, host real equality, a detached continuity oracle, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.ModulusContinuityUp.TasteGate.ModulusContinuityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Modulus-continuity NameCert obligations]
\label{thm:modulus-continuity-namecert-obligations}
For every accepted $\ModulusContinuityUp$ carrier $M=(G,S,K,D,Q,R,H,C,P,N)$, the local $\NameCert_{\ModulusContinuityUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the continuous-map graph, source StreamName window, CauchyModulus tolerance-to-window row, dyadic tolerance ledger, RegSeqRat readback, Real target seal, transport, replay, provenance, and local naming row;
\item classifier transport, requiring componentwise $\hsame$ transport in $H$ and displayed $\Cont$ replay in $C$ to preserve the ordered route $D,K,S,G,Q,R$;
\item modulus-row stability, requiring every target tolerance read from $D$ to select its source-window budget only through the displayed row $K$ and never through an external continuity oracle;
\item continuity-window handoff, requiring every graph read in $G$ and every regular readback in $Q$ to consume the source window $S$ selected by $K$ before the target seal $R$ is exposed;
\item ledger non-escape, requiring $P$ and $N$ to export no open-cover compactness, selected limit, quotient stream equality, host real equality, detached continuity oracle, or ambient Real completeness.
\end{enumerate}
No local NameCert obligation is stored outside those rows.
\end{theorem}
\leanchecked{BEDC.Derived.ModulusContinuityUp.ModulusContinuityTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:modulus-continuity-carrier}. The visible packet consists of the continuous-map graph $G$, the finite source-window row $S$, the Cauchy modulus row $K$, the dyadic ledger $D$, the readback row $Q$, the terminal Real seal $R$, and the structural rows $H,C,P,N$.

Classifier transport is structural. Componentwise $\hsame$ in $H$ preserves each displayed coordinate, and displayed $\Cont$ replay in $C$ repeats the same ordered route $D,K,S,G,Q,R$ for every accepted tolerance request.

Modulus-row stability is forced by the placement of $K$. A target tolerance may be read from $D$, but the only row that converts it into a source-window budget is the displayed $\CauchyModulusUp$ row, so no detached continuity oracle can enter the carrier.

The continuity-window handoff follows next. The graph row $G$ and the regular readback row $Q$ are exposed only after the window $S$ selected by $K$ has been displayed, and the Real target seal $R$ is reached only after those finite observations are replayed.

Finally, provenance is exhausted by $P$ and $N$. Since the carrier has no coordinate for open-cover compactness, selected limits, quotient stream equality, host real equality, a detached continuity oracle, or ambient Real completeness, the local certificate cannot export any such object.
\end{proof}

\begin{theorem}[Modulus-continuity Real and Completion handoff]
\label{thm:modulus-continuity-real-completion-handoff}
Every Real or Completion consumer of an accepted $\ModulusContinuityUp$ carrier reads the function-specific modulus only through the displayed rows
$$
\ContinuousMapUp,\ \CauchyModulusUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Consequently the consumer receives a finite tolerance-to-window route for the named function and no open-cover compactness, selected limit, quotient stream equality, host real equality, detached continuity oracle, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $M=(G,S,K,D,Q,R,H,C,P,N)$. Carrier projection gives a Real or Completion consumer access to the function-specific modulus only through those displayed rows.

The tolerance route starts in $D$. The target dyadic tolerance is converted into a finite source-window budget by $K$, and that budget identifies the source window $S$ before any graph read is available.

The graph and readback route then passes through $G$ and $Q$. These rows expose only the finite observations admitted by the selected window and the regular rational readback attached to it; the terminal Real target seal $R$ is downstream of that replay.

The remaining rows do not add mathematical primitives. The $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows transport, replay, source, and name the same finite route, so no excluded compactness, limit, quotient, host-equality, oracle, or completeness coordinate can be inserted.
\end{proof}
\leanchecked{BEDC.Derived.ModulusContinuityUp.ModulusContinuityRealCompletion\_handoff}

\begin{theorem}[Modulus-continuity composition route]
\label{thm:modulus-continuity-composition-route}
Let
$$
M_f=(G_f,S_f,K_f,D_f,Q_f,R_f,H_f,C_f,P_f,N_f)
$$
and
$$
M_g=(G_g,S_g,K_g,D_g,Q_g,R_g,H_g,C_g,P_g,N_g)
$$
be accepted $\ModulusContinuityUp$ carriers. Suppose the target seal exposed by $M_f$ is the source window and readback surface consumed by $M_g$. Then every target tolerance request for the composed Real or Completion consumer factors through the finite route
$$
D_g \to K_g \to S_g \to G_g \to Q_g \to D_f \to K_f \to S_f \to G_f \to Q_f \to R_f .
$$
The composed route uses only the displayed $\ContinuousMapUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the two carriers.
\end{theorem}
\begin{proof}
Project the second carrier first. By \autoref{thm:modulus-continuity-namecert-obligations}, the request for the outer target tolerance starts in $D_g$, is converted by $K_g$ into the finite window $S_g$, and reaches the graph and readback rows only through $G_g$ and $Q_g$.

Use the stated seal match to hand the consumed source surface of $M_g$ to the target surface of $M_f$. The handoff theorem \autoref{thm:modulus-continuity-real-completion-handoff} says that this surface is not a free Real or Completion oracle; it is read only through the displayed rows of $M_f$.

Project the first carrier along the same finite pattern. The matching request therefore passes through $D_f$, then $K_f$, then $S_f$, then $G_f$ and $Q_f$, and only after those finite rows have been replayed does it reach the terminal Real seal $R_f$.

The structural rows add no new primitive. The $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates in $M_f$ and $M_g$ transport and name the two projected routes, so their concatenation is still a finite tolerance-to-window route built from the displayed carrier rows alone.
\end{proof}

\begin{closurestatus}{\ModulusContinuityUp}
  \constructivestory{A $\ModulusContinuityUp$ packet is generated from a ContinuousMap graph row, a source StreamName window, a CauchyModulus tolerance-to-window row, a DyadicRatCore tolerance ledger, RegSeqRat readback, a Real target seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:modulus-continuity-carrier}, \autoref{thm:modulus-continuity-namecert-obligations}, \autoref{thm:modulus-continuity-real-completion-handoff}, and \autoref{thm:modulus-continuity-composition-route} seed the finite function-specific modulus route for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected limits, quotient stream equality, host real equality, ambient $\RealUp$ completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires carrier admission, classifier transport, modulus-row stability, continuity-window handoff, and ledger non-escape proofs for the same packet.}
\end{closurestatus}
