\chapter{A Concrete Naming Certificate for $\FilterRefinementUp$}
\label{ch:concrete-instances-filter-refinement-namecert}
\origin{human}

Following Kelley and Bourbaki on finer filters, cofinal subfilters, and refinement of directed bases, the $\FilterRefinementUp$ packet names the finite L10 bridge by which a completion route replaces one displayed filter base by a cofinal refinement. It sits after the finite base surface of \autoref{ch:concrete-instances-filterbase-namecert}, refines the Cauchy-filter route of \autoref{ch:concrete-instances-cauchyfilter-namecert}, and keeps the completion-facing consumers of \autoref{ch:concrete-instances-uniformcompletion-namecert}, \autoref{ch:concrete-instances-metriccompletion-namecert}, and \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert} on the displayed finite route. The packet records cofinal comparison rows only; it is not a quotient filter, not an ultrafilter, not a selected limit, not countable choice, and not an ambient completeness principle.

\begin{definition}[FilterRefinement NameCert surface]
\label{def:filter-refinement-namecert-surface}
A $\FilterRefinementUp$ carrier is a finite $\BHist$ packet
$$
R=(S,T,\rho,\lambda,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\FilterBaseUp$ row naming the base packets through which the original $\CauchyFilterUp$ or completion-facing route is read.
\item $T$ is the target $\FilterBaseUp$ row naming the refined base packets that will be exposed to downstream consumers.
\item $\rho$ is the cofinal refinement map. For each displayed target base packet it names a source base packet and the containment read from the target packet into that source packet.
\item $\lambda$ is the reverse comparison ledger when present. It records the displayed return comparisons needed for equivalence of two routes, but the carrier may leave this row empty when only one-way refinement is asserted.
\item $H$ records componentwise $\hsame$ transport for the source base, target base, cofinal refinement map, optional reverse ledger, continuation rows, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from an original base request through the cofinal refinement map and, when present, through the reverse comparison ledger.
\item $P$ is the $\Pkg$ provenance over $\FilterBaseUp$, $\CauchyFilterUp$, $\UniformCompletionUp$, $\MetricCompletionUp$, $\CauchyFilterCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FilterRefinementUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,T,\rho,\lambda,H,C,P,N$. There is no coordinate for quotient filters, ultrafilters, selected limits, countable choice, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.FilterRefinementUp.FilterRefinementTasteGate\_single\_carrier\_alignment}

\begin{theorem}[FilterRefinement Cauchy preservation]
\label{thm:filter-refinement-cauchy-preservation}
Let $R=(S,T,\rho,\lambda,H,C,P,N)$ be an accepted $\FilterRefinementUp$ carrier. If a $\CauchyFilterUp$ route is Cauchy through the displayed source base row $S$, then the route obtained by replaying every base request through the cofinal refinement map $\rho$ is Cauchy through the displayed target base row $T$.

The preserved Cauchy route uses only the finite refinement display
$$
T \xrightarrow{\rho} S \longmapsto H,C,P,N .
$$
It does not use a quotient filter, ultrafilter, selected limit, countable-choice selector, or ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.FilterRefinementUp.FilterRefinement\_cauchy\_preservation}
\begin{proof}
Project the accepted carrier of \autoref{def:filter-refinement-namecert-surface}. The source and target bases are displayed $\FilterBaseUp$ rows, and the cofinal map $\rho$ is a finite row of the same packet.

Start with a Cauchy request on the refined route. The target base packet requested from $T$ is sent by $\rho$ to a source base packet in $S$, together with the displayed containment read from the refined packet into the source packet.

Apply the Cauchy evidence already available on the source route. Because the source route is Cauchy through $S$, every precision or late-window request is discharged by a displayed source base packet and its $\CauchyFilterUp$ evidence.

Replay the result along the containment read recorded by $\rho$. The componentwise $\hsame$ row $H$ transports the visible base, refinement, continuation, provenance, and naming coordinates, while the $\Cont$ row $C$ replays the request through the displayed target packet.

Thus every refined request is answered by a finite target-row request followed by the finite source-row Cauchy witness. No excluded filter, limit, choice, or completeness coordinate is available in the carrier, so Cauchy preservation remains internal to $S,T,\rho,H,C,P,N$.
\end{proof}
\leanchecked{BEDC.Derived.FilterRefinementUp.FilterRefinementCauchyPreservation}

\begin{theorem}[FilterRefinement completion route]
\label{thm:filter-refinement-completion-route}
Let $R=(S,T,\rho,\lambda,H,C,P,N)$ be an accepted $\FilterRefinementUp$ carrier. Every $\UniformCompletionUp$, $\MetricCompletionUp$, or $\CauchyFilterCompletionUp$ consumer that receives the refined route sees only the finite target base row $T$, the cofinal refinement row $\rho$, the optional reverse ledger $\lambda$ when route equivalence is needed, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\FilterRefinementUp}$ row.

Equivalently, completion-facing reads factor through
$$
S \xleftarrow{\rho} T \longmapsto \lambda,H,C,P,N ,
$$
with $\lambda$ omitted for one-way refinement claims. The consumer does not receive a quotient filter, a selected completion point, countable choice, host equality, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with a completion-facing consumer. Its route is required to read the refined base row $T$ before it can inspect Cauchy-filter or completion data, so the first public object is a displayed finite $\FilterBaseUp$ row.

The row $\rho$ supplies the only comparison back to the source route. When a consumer must compare the refined route with the original route, it reads the optional ledger $\lambda$; otherwise the one-way cofinal refinement row is the entire comparison surface.

Transport and replay do not enlarge the route. The row $H$ moves the listed coordinates componentwise, and $C$ replays base requests through the same displayed refinement rows. The provenance row $P$ names the allowed completion consumers, while $N$ names the local certificate surface.

Consequently $\UniformCompletionUp$, $\MetricCompletionUp$, and $\CauchyFilterCompletionUp$ consumers receive a finite refinement route and no hidden completion object. Quotient filters, selected completion points, countable-choice selectors, host equality, and ambient completeness are not coordinates of $R$.
\end{proof}

\begin{closurestatus}{\FilterRefinementUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:filter-refinement-namecert-surface}, \autoref{thm:filter-refinement-cauchy-preservation}, and \autoref{thm:filter-refinement-completion-route} seed the finite filter-refinement bridge for Cauchy-filter and completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, ultrafilters, selected limits, countable choice, host equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, cofinal refinement coverage, optional reverse comparison compatibility, Cauchy preservation, completion-route exposure, and ledger-refusal proofs for BEDC.Derived.FilterRefinementUp.}
  \constructivestory{A $\FilterRefinementUp$ packet is generated from source and target FilterBase rows, a cofinal refinement map, an optional reverse comparison ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
