\chapter{A Concrete Naming Certificate for $\CauchyCompletionAssociativityUp$}
\label{ch:concrete-instances-cauchy-completion-associativity-namecert}
\origin{human}

Following Bishop--Bridges constructive completion together with Kelley/Bourbaki completion terminology, the $\CauchyCompletionAssociativityUp$ packet records the finite BEDC certificate for comparing two ways of flattening a triple Cauchy-completion route. It sits over the monadic transformer of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, the unit route of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the counit route of \autoref{ch:concrete-instances-cauchy-completion-counit-namecert}, the idempotence boundary of \autoref{ch:concrete-instances-cauchy-completion-idempotence-namecert}, and the minimality ledger of \autoref{ch:concrete-instances-cauchycompletionminimality-namecert}. It also consumes the finite-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a route-comparison certificate for repeated completion, not a quotient-completion equality, not a selected representative, not host equality of completed objects, not countable choice, and not ambient completeness of $\RealUp$.

\begin{definition}[CauchyCompletionAssociativity carrier]
\label{def:cauchy-completion-associativity-carrier}
A $\CauchyCompletionAssociativityUp$ carrier is a finite $\BHist$ packet
$$
A=(M,U,V,I,L,S,R,D,E,F,G,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $M$ is the $\CauchyCompletionMonadUp$ completion-transformer ledger used by all three displayed completion layers.
\item $U$ is the $\CauchyCompletionUnitUp$ row admitting the source-facing data into the first completion surface.
\item $V$ is the $\CauchyCompletionCounitUp$ row returning completion-facing reads to the displayed real-seal boundary.
\item $I$ is the $\CauchyCompletionIdempotenceUp$ row flattening any adjacent pair of completion layers to the same finite route.
\item $L$ is the $\CauchyCompletionMinimalityUp$ row recording that the flattened route is the least displayed completion service boundary consumed by downstream readers.
\item $S$ is the $\StreamNameUp$ finite-window row shared by the two flattening orders.
\item $R$ is the $\RegSeqRatUp$ readback row supplied after the shared stream windows and tolerance ledger have been consumed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by every precision request in the triple-completion route.
\item $E$ is the terminal $\RealUp$ seal reached by both displayed flattening orders.
\item $F$ records the left-associated route that first flattens the outer two completion layers and then flattens the result with the remaining layer.
\item $G$ records the right-associated route that first flattens the inner two completion layers and then flattens the result with the remaining layer.
\item $H$ records componentwise $\hsame$ transport for $M,U,V,I,L,S,R,D,E,F,G$ and the structural rows.
\item $C$ records displayed $\Cont$ replay from a triple-completion read through either $F$ or $G$ and then through the shared $U,V,I,L,S,D,R,E$ ledger.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionAssociativityUp$, $\CauchyCompletionMonadUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionCounitUp$, $\CauchyCompletionIdempotenceUp$, $\CauchyCompletionMinimalityUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionAssociativityUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected Cauchy representatives, host equality of completed objects, countable-choice schedules, open-cover compactness, ambient completeness, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CauchyCompletionAssociativity NameCert obligations]
\label{thm:cauchy-completion-associativity-namecert-obligations}
For an accepted $\CauchyCompletionAssociativityUp$ carrier $A=(M,U,V,I,L,S,R,D,E,F,G,H,C,P,N)$, the local $\NameCert_{\CauchyCompletionAssociativityUp}$ surface consists exactly of the following five finite rows:
\begin{enumerate}
\item carrier admission for the monad, unit, counit, idempotence, minimality, stream-window, regular-readback, dyadic-tolerance, real-seal, left-route, right-route, transport, replay, provenance, and local naming rows;
\item left-associated flattening, requiring the route $F$ to apply the idempotence row $I$ and then the counit/minimality ledger $V,L$ before the shared $S,D,R,E$ surface is exposed;
\item right-associated flattening, requiring the route $G$ to apply the same $I,V,L$ ledger in the other finite order before the shared $S,D,R,E$ surface is exposed;
\item classifier stability, requiring transported packets with the same $M,U,V,I,L,S,D,R,E,F,G$ rows to be identified by the displayed $\hsame$ and $\Cont$ data;
\item ledger non-escape, stating that no quotient completion equality, selected representative, host equality, countable-choice schedule, open-cover compactness principle, ambient-completeness theorem, or $\RealUp$ completeness theorem is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-associativity-carrier}. The tuple lists exactly the completion transformer, unit, counit, idempotence, minimality, shared observation rows, the two association routes, transport, replay, provenance, and local name.

For the left-associated route, read $F$ first. Its first replay flattens one adjacent pair of completion layers through $I$, then returns the resulting completion-facing read through $V$ and the minimal service boundary $L$ before the shared stream, dyadic, regular, and real-seal rows are consumed.

For the right-associated route, read $G$ first. It uses the same idempotence, counit, and minimality rows in the other finite order, and the replay row $C$ then sends the result to the same $S,D,R,E$ surface.

Classifier stability is componentwise transport along $H$ followed by replay through $C$. Since the carrier fields are exhausted by $M,U,V,I,L,S,R,D,E,F,G,H,C,P,N$, the excluded quotient, representative-selection, host-equality, choice, compactness, ambient-completeness, and real-completeness principles have no row from which a consumer could read them.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCompletionAssociativityUp.TasteGate.CauchyCompletionAssociativityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyCompletionAssociativity flattening route]
\label{thm:cauchy-completion-associativity-flattening-route}
Let $A=(M,U,V,I,L,S,R,D,E,F,G,H,C,P,N)$ be an accepted $\CauchyCompletionAssociativityUp$ carrier. The two finite routes from a triple completion to the single displayed completion factor through the same unit, counit, idempotence, and minimality ledger:
$$
\begin{aligned}
F&\longmapsto I\longmapsto V\longmapsto L\longmapsto S\longmapsto D\longmapsto R\longmapsto E,\\
G&\longmapsto I\longmapsto V\longmapsto L\longmapsto S\longmapsto D\longmapsto R\longmapsto E .
\end{aligned}
$$
Thus the visible associativity law is equality of the finite BEDC route through $M,U,V,I,L,S,D,R,E,H,C,P,N$, not equality of quotient completions, not host equality of completed metric objects, not a selected representative, and not countable choice or ambient completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The two route rows $F$ and $G$ are the only coordinates that distinguish the left-associated and right-associated flattening orders.

Read the ledger common to both routes. The idempotence row $I$ supplies the adjacent-pair flattening step, the counit row $V$ returns completion-facing reads to the displayed real-seal boundary, and the minimality row $L$ records that downstream consumers receive the least displayed completion service boundary.

After that common ledger, both routes consume the same observation surface. The finite windows are named by $S$, each precision request is accounted for by $D$, the regular rational readback is $R$, and the terminal seal is $E$.

Finally $M$ and $U$ record the surrounding completion-transformer and source-admission rows, while $H,C,P,N$ transport, replay, source, and name the same packet. No further coordinate remains for quotient equality, host equality, selected representatives, countable choice, or ambient completeness, so the two routes agree exactly on the displayed finite ledger.
\end{proof}

\begin{closurestatus}{\CauchyCompletionAssociativityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-associativity-carrier}, \autoref{thm:cauchy-completion-associativity-namecert-obligations}, and \autoref{thm:cauchy-completion-associativity-flattening-route} seed the finite associativity certificate for flattening triple Cauchy-completion routes through the shared unit, counit, idempotence, minimality, StreamName, RegSeqRat, DyadicRatCore, and Real ledgers.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.CauchyCompletionAssociativityUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, host equality of completed metric objects, countable choice, open-cover compactness, ambient completeness, or completeness of $\RealUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, left- and right-associated flattening, classifier stability, and ledger non-escape for BEDC.Derived.CauchyCompletionAssociativityUp.}
  \constructivestory{The construction starts with a triple-completion read, compares the left- and right-associated finite flattening rows, routes both through the same unit, counit, idempotence, and minimality ledger, and then exposes the shared StreamName, DyadicRatCore, RegSeqRat, and Real seal surface.}
\end{closurestatus}
