\chapter{A Concrete Naming Certificate for $\LocatedCauchyFilterUp$}
\label{ch:concrete-instances-located-cauchy-filter-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, and Kelley filterbase terminology, the $\LocatedCauchyFilterUp$ packet records the filter-level located witness surface used by the L10 completion route before any quotient filter, selected limit, countable-choice selector, host equality, or $\RealUp$ completeness principle is available. It sits between the Cauchy-filter carrier of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the basis-level witness rows of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert}, the regular filter route of \autoref{ch:concrete-instances-regularcauchyfilter-namecert}, and the sequence-level located witness of \autoref{ch:concrete-instances-located-cauchy-sequence-namecert}. Its finite readback path uses the stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the downstream real-name seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[Located Cauchy filter carrier]
\label{def:located-cauchy-filter-carrier}
A $\LocatedCauchyFilterUp$ carrier is a finite $\BHist$ packet
$$
L=(F,B,R,S,Q,D,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyFilterUp$ row naming the accepted Cauchy filter surface.
\item $B$ is the $\CauchyFilterBasisUp$ row that exposes finite basis neighborhoods and refinement witnesses.
\item $R$ is the $\RegularCauchyFilterUp$ row carrying the regular tail budget attached to the basis surface.
\item $S$ is the $\StreamNameUp$ finite-window row used by sequence-facing consumers.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the displayed windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger for located ball comparisons.
\item $T$ is the located tail row, recording the displayed witness that the filter basis eventually meets the requested dyadic ball.
\item $E$ is the downstream $\RealUp$ seal boundary, reachable only after $F,B,R,S,Q,D,T$ have been consumed.
\item $H$ records componentwise $\hsame$ transport for the filter, basis, regularity, window, readback, dyadic, located-tail, seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located precision request through $F,B,R,S,Q,D,T,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedCauchyFilterUp$, $\CauchyFilterUp$, $\CauchyFilterBasisUp$, $\RegularCauchyFilterUp$, $\LocatedCauchySequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCauchyFilterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for quotient filters, selected limits, countable choice, hidden infinite basis inspection, host real equality, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.LocatedCauchyFilterUp.LocatedCauchyFilterTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located Cauchy filter NameCert obligations]
\label{thm:located-cauchy-filter-namecert-obligations}
For every accepted $\LocatedCauchyFilterUp$ carrier $L=(F,B,R,S,Q,D,T,E,H,C,P,N)$, the local $\NameCert_{\LocatedCauchyFilterUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the Cauchy filter row, basis row, regular filter row, finite-window row, rational readback row, dyadic tolerance ledger, located-tail row, seal boundary, transport, continuation, provenance, and local naming row;
\item basis exposure, requiring every located request to read the displayed basis row $B$ only after the Cauchy filter row $F$ has been fixed;
\item regular-tail exactness, requiring the regular filter row $R$ and located-tail row $T$ to share the same basis request and dyadic tolerance ledger $D$;
\item sequence handoff compatibility, requiring $S$ and $Q$ to expose only finite windows and regular rational readbacks generated from the same located filter request;
\item transport replay, requiring $H$ and $C$ to preserve the route through $F,B,R,S,Q,D,T,E$ under componentwise $\hsame$ and displayed continuation;
\item real-seal non-escape, requiring every $\RealUp$-facing read to pass through the filter, basis, regularity, window, readback, dyadic, and located-tail rows before it reaches $E$;
\item provenance and name exhaustion, requiring $P$ and $N$ to name only this finite route and to export no quotient filters, selected limits, countable choice, hidden basis inspection, host equality, or ambient completeness.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-cauchy-filter-carrier}. The visible analytic rows are precisely the Cauchy filter, basis, regularity, stream-window, rational readback, dyadic tolerance, located-tail, and downstream seal rows.

For basis exposure, replay a located precision request through $C$. The request first fixes the Cauchy filter row $F$, then reads the finite basis neighborhoods in $B$; no sequence window or real-facing seal is available before this basis route is displayed.

Regular-tail exactness is read from $R,D,T$. The regular row $R$ records the tail budget over the same basis request, the dyadic ledger $D$ supplies the requested ball data, and the located-tail row $T$ witnesses that the basis eventually meets that displayed ball.

The sequence handoff uses only finite data. The rows $S$ and $Q$ expose the requested windows and regular rational readbacks downstream of $F,B,R,D,T$, so they cannot introduce hidden infinite basis inspection or a selected limit.

Finally, $H$ and $C$ preserve the same ordered route under transport and replay. The seal boundary $E$ appears only after $F,B,R,S,Q,D,T$, and the provenance and name rows $P,N$ have no coordinates for quotient filters, selected limits, countable choice, host equality, or ambient completeness.
\end{proof}

\begin{theorem}[Located Cauchy filter regular tail location]
\label{thm:located-cauchy-filter-regular-tail-location}
Let $L=(F,B,R,S,Q,D,T,E,H,C,P,N)$ be an accepted $\LocatedCauchyFilterUp$ carrier. Every regular-tail request in $R$ factors through the finite located route
$$
F,B,D \longmapsto T \longmapsto R \longmapsto S,Q,H,C,P,N .
$$
Thus the regular filter consumer receives a displayed Cauchy filter, a finite basis neighborhood, a dyadic tolerance ledger, and a located-tail witness before any sequence-facing readback or real-facing seal can be inspected.
\end{theorem}
\begin{proof}
Start with a regular-tail request. By \autoref{def:located-cauchy-filter-carrier}, the row $R$ is packaged with the Cauchy filter row $F$, the basis row $B$, the dyadic ledger $D$, and the located-tail row $T$.

Apply the basis exposure and regular-tail exactness clauses of \autoref{thm:located-cauchy-filter-namecert-obligations}. The request fixes $F$ and $B$, then reads the dyadic ball data in $D$, and only then consumes the located witness $T$ attached to that same basis request.

The remaining rows are downstream support. The sequence windows $S$, rational readbacks $Q$, transport $H$, replay $C$, provenance $P$, and local name $N$ preserve and package the same finite route; none of them adds a quotient filter, selected limit, countable-choice selector, hidden basis inspection, host equality, or ambient completeness witness.
\end{proof}

\begin{theorem}[Located Cauchy filter basis-refinement route]
\label{thm:located-cauchy-filter-basis-refinement-route}
Every located-tail read $T$ in an accepted $\LocatedCauchyFilterUp$ packet
$$
L=(F,B,R,S,Q,D,T,E,H,C,P,N)
$$
first fixes the $\CauchyFilterUp$ row $F$, then refines through the $\CauchyFilterBasisUp$ row $B$ at the displayed dyadic tolerance $D$, and only then exposes the $\RegularCauchyFilterUp$ row $R$, $\StreamNameUp$ windows $S$, $\RegSeqRatUp$ readback $Q$, and $\RealUp$ seal row $E$.
\end{theorem}
\begin{proof}
Project the carrier. The located-tail coordinate $T$ is packaged with exactly one Cauchy filter row $F$, one basis row $B$, one dyadic tolerance ledger $D$, and the downstream rows $R,S,Q,E,H,C,P,N$.

Use the basis exposure clause of \autoref{thm:located-cauchy-filter-namecert-obligations}. A located request fixes $F$ before it may inspect the displayed basis row $B$.

Use the regular-tail exactness clause of the same theorem. The basis refinement is read at the dyadic tolerance recorded in $D$, and the located-tail row $T$ shares that displayed request before $R,S,Q$ or $E$ are available.

The remaining rows only preserve or consume the finite route. Hence quotient filters, selected limits, countable choice, hidden basis inspection, host equality, and ambient completeness are absent from the refinement path.
\end{proof}

\begin{theorem}[Located Cauchy filter Real seal boundary]
\label{thm:located-cauchy-filter-real-seal-boundary}
Every $\RealUp$-facing read exported by an accepted $\LocatedCauchyFilterUp$ carrier factors through the complete finite route
$$
F,B,R,S,Q,D,T,E,H,C,P,N.
$$
Consequently a downstream consumer cannot read the terminal real-name seal without also reading the Cauchy filter row, basis row, regular tail budget, finite stream windows, regular rational readback, dyadic tolerance ledger, located-tail witness, componentwise transport, displayed continuation, provenance, and local NameCert row.
\end{theorem}
\begin{proof}
Begin with a downstream real-facing read. The carrier exposes the seal only as $E$, and $E$ is listed after the filter, basis, regularity, window, readback, dyadic, and located-tail rows in \autoref{def:located-cauchy-filter-carrier}.

Use the real-seal non-escape clause of \autoref{thm:located-cauchy-filter-namecert-obligations}. Any request that reaches $E$ must first pass through $F,B,R,S,Q,D,T$, so the terminal seal is a routed finite read rather than a host-selected limit.

The structural rows then preserve the route. The rows $H,C,P,N$ transport, replay, source, and name the same displayed packet, and the carrier has no coordinate for quotient filters, countable choice, hidden basis inspection, host equality, or ambient $\RealUp$ completeness.
\end{proof}

\closureat{LocatedCauchyFilterUp}{seedStr}

\begin{closurestatus}{\LocatedCauchyFilterUp}
  \constructivestory{A $\LocatedCauchyFilterUp$ packet is generated from a CauchyFilter row, a CauchyFilterBasis row, a RegularCauchyFilter tail budget, finite StreamName windows, RegSeqRat readbacks, a DyadicRatCore tolerance ledger, a located-tail witness, a Real seal boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-cauchy-filter-carrier}, \autoref{thm:located-cauchy-filter-namecert-obligations}, \autoref{thm:located-cauchy-filter-regular-tail-location}, \autoref{thm:located-cauchy-filter-basis-refinement-route}, and \autoref{thm:located-cauchy-filter-real-seal-boundary} seed the filter-level located Cauchy packet between CauchyFilter, CauchyFilterBasis, RegularCauchyFilter, LocatedCauchySequence, StreamName, RegSeqRat, DyadicRatCore, and Real consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filter equality, selected limits, countable choice, hidden infinite basis inspection, host real equality, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Lean closure requires carrier admission, the NameCert obligation surface, regular-tail location, and Real seal boundary for BEDC.Derived.LocatedCauchyFilterUp.}
\end{closurestatus}
