\chapter{A Concrete Naming Certificate for $\DenseUniformEmbeddingUp$}
\label{ch:concrete-instances-dense-uniform-embedding-namecert}
\origin{human}

Following the Bourbaki and Kelley treatment of uniform completions, and the Bishop--Bridges constructive use of dense uniform embeddings, the $\DenseUniformEmbeddingUp$ packet records the finite interface by which a source uniform or metric object enters a separated completion as a dense uniformly controlled subobject. It binds the dense embedding surface of \autoref{ch:concrete-instances-completionembedding-namecert}, the completion target of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the modulus route of \autoref{ch:concrete-instances-uniformcontinuity-namecert}, the extension consumer of \autoref{ch:concrete-instances-uniform-continuous-extension-namecert}, and the separated target boundary of \autoref{ch:concrete-instances-separatedcompletion-namecert}. The packet is a NameCert carrier for the L10 completion route; it is not a quotient completion, a representative selector, or an assertion of ambient completeness.

\begin{definition}[DenseUniformEmbedding carrier]
\label{def:dense-uniform-embedding-carrier}
A $\DenseUniformEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
D=(S,T,I,Q,M,E,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source uniform or metric data row whose point histories, entourages, and metric observations supply the dense domain.
\item $T$ is the target separated completion data row, read through the $\UniformCompletionUp$ and $\SeparatedCompletionUp$ surfaces before any consumer treats target reads as separated completion reads.
\item $I$ is the dense image witness row, recording that every displayed target tolerance window has a source-side image window.
\item $Q$ is the uniform-continuity modulus row, read through $\UniformContinuityUp$, that transports source closeness to target closeness along the displayed image route.
\item $M$ is the $\CompletionEmbeddingUp$ handoff row by which source observations enter the completion-facing target route.
\item $E$ is the $\UniformContinuousExtensionUp$ consumer row naming the downstream extension interface that may read the dense source and target separated completion together.
\item $U$ is the local compatibility row stating that $I,Q,M,E$ are read over the same source row $S$ and target row $T$.
\item $H$ records componentwise $\hsame$ transport for $S,T,I,Q,M,E,U$ and for the structural rows.
\item $C$ records displayed $\Cont$ replay from source histories through dense image, uniform modulus, completion embedding handoff, extension consumer, and separated completion target.
\item $P$ is the $\Pkg$ provenance over $\DenseUniformEmbeddingUp$, $\UniformCompletionUp$, $\SeparatedCompletionUp$, $\CompletionEmbeddingUp$, $\UniformContinuityUp$, $\UniformContinuousExtensionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\DenseUniformEmbeddingUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completions, selected representatives, host equality, countable choice, ambient completeness, or a detached target-completion object.
\end{definition}
\leanchecked{BEDC.Derived.DenseUniformEmbeddingUp.DenseUniformEmbeddingTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DenseUniformEmbedding NameCert obligations]
\label{thm:dense-uniform-embedding-namecert-obligations}
For every accepted $\DenseUniformEmbeddingUp$ carrier $D=(S,T,I,Q,M,E,U,H,C,P,N)$, the local $\NameCert_{\DenseUniformEmbeddingUp}$ surface consists exactly of these finite obligation rows:
\begin{enumerate}
\item carrier admission for the source uniform or metric row, target separated completion row, dense image witness, uniform-continuity modulus, completion embedding handoff, extension consumer, compatibility row, hsame transport, Cont replay, package provenance, and local naming;
\item dense image coverage, requiring each target tolerance request in $T$ to route through the source image witness $I$ before any separated completion read is exported;
\item uniform-modulus stability, requiring every source closeness read consumed by the dense route to pass through $Q$ before it reaches the target side;
\item completion-embedding compatibility, requiring the handoff row $M$ to be the only route from source observations into the completion-facing target;
\item extension-consumer compatibility, requiring every $\UniformContinuousExtensionUp$ consumer to read the same $S,T,I,Q,M$ route before using $E$;
\item transport and replay preservation, requiring $H$ and $C$ to preserve the ordered route under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item ledger non-escape, excluding quotient completions, selected representatives, host equality, countable choice, ambient completeness, and detached target-completion data.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dense-uniform-embedding-carrier}. The tuple lists the source row, target separated completion row, dense image witness, modulus, completion handoff, extension consumer, compatibility row, transport, replay, provenance, and local naming.

Dense image coverage is read from $I$ over the same target row $T$. A target tolerance request cannot be consumed until the packet has displayed a source-side image window for that request.

Uniform-modulus stability is the row $Q$. It is the only route by which source closeness is transported to target closeness, so every completion-facing dense read must pass through $Q$ before reaching the target side.

The completion and extension boundaries are the rows $M$ and $E$. The handoff row $M$ admits source observations into the completion-facing route, and the extension row $E$ is read only after $S,T,I,Q,M$ have been fixed by $U$.

Finally, $H,C,P,N$ record transport, replay, provenance, and local naming for exactly those rows. Since the carrier contains no quotient, selected representative, host equality, choice, ambient-completeness, or detached-completion coordinate, the listed obligations exhaust the NameCert surface.
\end{proof}

\begin{theorem}[DenseUniformEmbedding completion consumer route]
\label{thm:dense-uniform-embedding-completion-consumer-route}
Every completion or extension consumer of an accepted $\DenseUniformEmbeddingUp$ packet factors through the finite route
$$
S\longmapsto I\longmapsto Q\longmapsto M\longmapsto T\longmapsto E\longmapsto H,C,P,N .
$$
Thus the consumer receives a dense uniformly controlled source image inside the separated completion target, not a quotient-completion point, selected representative, host equality witness, countable-choice schedule, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the source row $S$. The consumer may read only the displayed source uniform or metric histories supplied by the packet.

The dense image row $I$ and uniform-modulus row $Q$ are the next route components. They turn a target tolerance request into a source image window and transport source closeness to target closeness.

The completion embedding handoff $M$ then sends the controlled source observations into the completion-facing boundary. The target row $T$ is reached only after this dense uniform route has been recorded.

Finally the extension consumer row $E$ may read the same route, while $H,C,P,N$ preserve and name it. No excluded quotient, representative, host equality, choice, or ambient completeness object has a coordinate in the carrier, so no consumer can escape the displayed route.
\end{proof}

\begin{theorem}[DenseUniformEmbedding ledger non-escape]
\label{thm:dense-uniform-embedding-ledger-nonescape}
For every accepted $\DenseUniformEmbeddingUp$ carrier $D=(S,T,I,Q,M,E,U,H,C,P,N)$, every exported read remains inside the rows
$$
S,T,I,Q,M,E,U,H,C,P,N
$$
of \autoref{def:dense-uniform-embedding-carrier}. The packet exports no quotient completion, selected representative, host equality, countable-choice selector, ambient completeness witness, or detached completion object.
\end{theorem}
\begin{proof}
The NameCert obligations of \autoref{thm:dense-uniform-embedding-namecert-obligations} enumerate every admissible carrier, coverage, modulus, handoff, extension, transport, replay, provenance, and naming row.

The completion consumer route of \autoref{thm:dense-uniform-embedding-completion-consumer-route} covers each downstream read by forcing it through $S,I,Q,M,T,E,H,C,P,N$. The compatibility row $U$ states that these route components are read over the same source and target rows.

There is no remaining carrier coordinate from which a consumer could project a quotient class, selected representative, host equality judgement, choice schedule, ambient-completeness theorem, or detached completion object. Therefore every exported read stays within the displayed finite ledger.
\end{proof}

\begin{closurestatus}{\DenseUniformEmbeddingUp}
  \constructivestory{A $\DenseUniformEmbeddingUp$ packet is generated from a source uniform or metric row, a target UniformCompletion and SeparatedCompletion row, a dense image witness, a UniformContinuity modulus, a CompletionEmbedding handoff, a UniformContinuousExtension consumer row, route compatibility, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dense-uniform-embedding-carrier}, \autoref{thm:dense-uniform-embedding-namecert-obligations}, \autoref{thm:dense-uniform-embedding-completion-consumer-route}, and \autoref{thm:dense-uniform-embedding-ledger-nonescape} seed the dense uniform embedding interface for the L10 completion route.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.DenseUniformEmbeddingUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, host equality, countable choice, ambient completeness, or detached target-completion objects.}
  \upgradepath{Obligation closure requires checked carrier admission, dense image coverage, uniform-modulus stability, completion-embedding compatibility, extension-consumer compatibility, transport replay, and ledger non-escape for BEDC.Derived.DenseUniformEmbeddingUp.}
\end{closurestatus}
