\chapter{A Concrete Naming Certificate for $\CauchyRepresentationUp$}
\label{ch:concrete-instances-cauchy-representation-namecert}
\origin{human}

Following Bishop and Bridges and the computable-analysis convention of representing reals by effective Cauchy names, the $\CauchyRepresentationUp$ packet records the finite interface through which stream windows, regular rational readbacks, dyadic tolerances, and a terminal real seal are presented to represented-space consumers. It sits between the stream-name certificate of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational sequence boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the represented-space surface of \autoref{ch:concrete-instances-representedspace-namecert}. The packet supplies a standard Cauchy-representation boundary without identifying it with $\ComputableRealUp$, $\BishopRealUp$, or the completed $\RealUp$ object.

\begin{definition}[CauchyRepresentation carrier]
\label{def:cauchy-representation-carrier}
A $\CauchyRepresentationUp$ carrier is a finite $\BHist$ packet
$$
K=(S,W,R,D,A,G,H,C,P,E,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ source row. It records the certified stream name whose finite windows are inspected.
\item $W$ is the finite window schedule opened from $S$ at the requested observation indices and precision levels.
\item $R$ is the $\RegSeqRatUp$ readback row turning the displayed stream windows into regular rational observations.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare the regular rational observations at the displayed scales.
\item $A$ is the $\RealUp$ seal row reached only after $S,W,R,D$ have been replayed.
\item $G$ is the $\RepresentedSpaceUp$-facing source row, recording that the same finite name is being offered as a represented-space source rather than as a host real or quotient stream.
\item $H$ records componentwise $\hsame$ transport for the stream source, window schedule, regular readback, dyadic tolerance ledger, real seal, represented-space source row, continuation row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from source-window inspection through regular readback, dyadic tolerance comparison, represented-space exposure, and the final seal handoff.
\item $P$ is the $\Pkg$ provenance over $\CauchyRepresentationUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\RepresentedSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $E$ is the local evidence row recording that every represented-space read of the packet factors through the same $S,W,R,D,A$ route.
\item $N$ is the local $\NameCert_{\CauchyRepresentationUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite Cauchy-representation packet. It has no coordinate for quotient streams, selected limits, host real equality, countable choice, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.CauchyRepresentationUp.CauchyRepresentationTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyRepresentation NameCert obligations]
\label{thm:cauchy-representation-namecert-obligations}
For every accepted $\CauchyRepresentationUp$ carrier $K=(S,W,R,D,A,G,H,C,P,E,N)$, the local $\NameCert_{\CauchyRepresentationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the stream source, finite window schedule, regular rational readback, dyadic tolerance ledger, real seal, represented-space source row, transport, replay, provenance, evidence, and local naming rows;
\item window exactness, requiring each finite observation to be read first through $S$ and $W$ before any regular rational row is consulted;
\item regular readback exactness, requiring $R$ to expose only the rational observations generated by the displayed stream windows;
\item dyadic tolerance exactness, requiring $D$ to record the finite tolerance comparisons used to justify the regular readback route;
\item real-seal non-escape, requiring $A$ to remain downstream of $S,W,R,D$ and never to serve as a host-level selected limit;
\item represented-space source compatibility, requiring $G$ and $E$ to expose the same finite route to $\RepresentedSpaceUp$ consumers;
\item componentwise transport, replay, provenance, and local naming, requiring $H,C,P,N$ to preserve and name exactly the displayed packet;
\item refusal of quotient streams, selected limits, host real equality, countable choice, and ambient completeness as local NameCert data.
\end{enumerate}
No Cauchy-representation obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The finite analytic route is exactly the stream row $S$, the window schedule $W$, the regular rational readback $R$, the dyadic tolerance ledger $D$, and the seal row $A$.

Window exactness and regular readback exactness follow from this route order. A consumer cannot reach $R$ without first displaying the finite window schedule opened from $S$, and the tolerance ledger $D$ reads only the regular observations exposed by $R$.

The represented-space boundary is carried by $G$ and $E$. These rows expose the same finite route to represented-space consumers, so they do not add a second source of limits or equality.

Finally, $H,C,P,N$ transport, replay, package, and name the packet without adding rows. Since the carrier contains no coordinate for quotient streams, selected limits, host real equality, countable choice, or ambient completeness, none of those readings can become a local obligation.
\end{proof}

\begin{theorem}[CauchyRepresentation stream and regular handoff]
\label{thm:cauchy-representation-streamname-regseqrat-handoff}
Let $K=(S,W,R,D,A,G,H,C,P,E,N)$ be an accepted $\CauchyRepresentationUp$ carrier. Every $\RepresentedSpaceUp$- or $\RealUp$-facing read of $K$ factors through the finite handoff route
$$
S,W \longmapsto R \longmapsto D \longmapsto A \longmapsto G,E,H,C,P,N .
$$
Thus the stream name and regular rational readback are the only source rows by which the real seal and represented-space exposure are reached. The route contains no quotient stream, selected limit, host real equality, countable-choice selector, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with a consumer read of the packet. Carrier admission gives access to the seal and represented-space rows, but only as rows in the same finite packet as $S,W,R,D$.

Replay the continuation row $C$. The read first opens the $\StreamNameUp$ source and its finite schedule, then consumes the $\RegSeqRatUp$ readback, and then consults the $\DyadicRatCoreUp$ tolerance ledger.

Only after this replay can the $\RealUp$ seal row and the $\RepresentedSpaceUp$-facing row be read. The evidence, transport, provenance, and local naming rows preserve that same route, so the consumer receives no quotient stream, selected limit, host real equality, countable choice, or ambient completeness data.
\end{proof}

\begin{closurestatus}{\CauchyRepresentationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-representation-carrier}, \autoref{thm:cauchy-representation-namecert-obligations}, and \autoref{thm:cauchy-representation-streamname-regseqrat-handoff} seed the finite Cauchy-representation boundary over $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerances, a $\RealUp$ seal row, and $\RepresentedSpaceUp$ exposure.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, host real equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, window exactness, regular readback exactness, dyadic tolerance exactness, seal non-escape, represented-space compatibility, transport, replay, provenance, and local naming for BEDC.Derived.CauchyRepresentationUp.}
  \constructivestory{A $\CauchyRepresentationUp$ packet is generated from a $\StreamNameUp$ source, finite stream windows, a $\RegSeqRatUp$ readback row, a $\DyadicRatCoreUp$ tolerance ledger, a $\RealUp$ seal row, a $\RepresentedSpaceUp$ source row, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, a local evidence row, and a local $\NameCert$ row.}
\end{closurestatus}
