\chapter{A Concrete Naming Certificate for $\RealBaireCylinderUp$}
\label{ch:concrete-instances-real-baire-cylinder-namecert}
\origin{human}

Following Brouwer's finite-prefix reading of choice sequences and the Bishop--Bridges insistence that real-number data be displayed by effective finite approximations, the $\RealBaireCylinderUp$ packet names a Baire-prefix cylinder only through the finite rows that a Real-facing consumer can inspect. It sits after the prefix-cylinder surface of \autoref{ch:concrete-instances-bairespace-namecert}, the finite-window schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite readback boundary for the open Real and Completion route; it is not a quotient stream, a host function equality, a countable-choice selector, a completed Baire branch, or a Real completeness theorem.

\begin{definition}[Real Baire-cylinder carrier]\label{def:real-baire-cylinder-carrier}
A $\RealBaireCylinderUp$ carrier is a finite $\BHist$ packet
$$
R=(B,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is a $\BaireSpaceUp$ prefix packet. It records the finite natural-index window, displayed unary answer rows, prefix-cylinder classifier, and local Baire ledger.
\item $S$ is the $\StreamNameUp$ finite-window row selected from $B$. It exposes the scheduled requests that a Real-facing read is allowed to replay.
\item $Q$ is the $\RegSeqRatUp$ readback row. It converts the selected stream window into the regular rational approximation rows visible to the Real route.
\item $E$ is the $\RealUp$ seal. It is reached only after the Baire prefix, StreamName window, and RegSeqRat readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the Baire prefix packet, StreamName window, RegSeqRat readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite Real-facing request back through $E,Q,S,B$.
\item $P$ is the $\Pkg$ provenance over $\RealBaireCylinderUp$, $\BaireSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealBaireCylinderUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,S,Q,E,H,C,P,N$. It has no coordinate for host sequence equality, quotient real equality, countable choice, ambient completeness, or a tail of the Baire stream outside the displayed prefix window.
\end{definition}
\leanchecked{BEDC.Derived.RealBaireCylinderUp.TasteGate.RealBaireCylinderTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Real Baire-cylinder NameCert obligations]\label{thm:real-baire-cylinder-namecert-obligations}
For every accepted $\RealBaireCylinderUp$ carrier $R=(B,S,Q,E,H,C,P,N)$, the local $\NameCert_{\RealBaireCylinderUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the displayed BaireSpace prefix packet, StreamName finite window, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming rows;
\item prefix-cylinder stability, requiring every transported read to remain inside the finite Baire prefix packet $B$ and its displayed classifier rows;
\item StreamName handoff, requiring every Real-facing request to select its finite schedule through $S$ before any regular rational readback is exposed;
\item RegSeqRat readback, requiring the scheduled window to pass through $Q$ before the Real seal can be read;
\item Real-seal non-escape, requiring $E$ to seal only the displayed readback route and to expose no host real equality, selected limit, countable choice, or ambient completeness principle;
\item provenance exhaustion, requiring $P$ and $N$ to name only $B,S,Q,E,H,C$ and to export no principle absent from those rows.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-baire-cylinder-carrier}. The projected rows are exactly the Baire prefix packet $B$, the StreamName finite window $S$, the RegSeqRat readback $Q$, the Real seal $E$, and the structural rows $H,C,P,N$.

Prefix-cylinder stability is inherited from the BaireSpace packet. Transport may change the displayed rows only through the componentwise $\hsame$ data named by $H$ and replayed by $C$, so a transported request remains inside the same finite prefix-cylinder surface.

The StreamName handoff and RegSeqRat readback are ordered by the carrier itself. A Real-facing request first chooses the finite window $S$ from $B$, then reads the regular rational approximation data through $Q$.

Finally the seal row $E$ is downstream of $Q$. Since $P$ and $N$ name only this route, there is no carrier coordinate from which a tail stream, quotient equality, countable-choice selector, selected limit, or ambient completeness theorem can be exported.
\end{proof}

\begin{theorem}[Real Baire-cylinder stream-real handoff]\label{thm:real-baire-cylinder-stream-real-handoff}
Let $R=(B,S,Q,E,H,C,P,N)$ be an accepted $\RealBaireCylinderUp$ carrier. Every $\RealUp$-facing read exported by $R$ factors through the finite route
$$
B \longmapsto S \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus a consumer receives a $\BaireSpaceUp$ prefix packet, then a $\StreamNameUp$ finite window, then a $\RegSeqRatUp$ readback, and only then the terminal $\RealUp$ seal. No read can bypass this route through host function equality, quotient streams, countable choice, or Real completeness.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$-facing read of $R$. By \autoref{def:real-baire-cylinder-carrier}, the only Real coordinate is $E$, and $E$ is placed after the prefix packet $B$, the finite window $S$, and the regular rational readback $Q$.

The Baire prefix supplies only the displayed finite cylinder rows. The StreamName row selects the schedule coordinates available to the consumer, and the RegSeqRat row converts that scheduled window into the rational readback visible to the Real route.

The rows $H,C,P,N$ transport, replay, name, and record the same dependency order. Therefore every Real-facing read factors through the displayed prefix-window route and cannot expose any excluded host or completeness datum.
\end{proof}

\falsifiablePrediction{Every $\RealBaireCylinderUp$ Real-facing read factors through a BaireSpace prefix packet, StreamName finite window, RegSeqRat readback, RealUp seal, transport, replay, provenance, and local naming row.}

\independenceWitness{bairespace, streamname, regseqrat, real: $\RealBaireCylinderUp$ is not bijective to any listed sibling because it jointly carries Baire prefix-cylinder data, finite stream-window selection, regular rational readback, Real sealing, transport, replay, provenance, and local naming.}

\closureat{RealBaireCylinderUp}{seedStr}

\begin{closurestatus}{\RealBaireCylinderUp}
  \constructivestory{A $\RealBaireCylinderUp$ packet is generated from a BaireSpace prefix packet, a StreamName finite window, a RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-baire-cylinder-carrier}, \autoref{thm:real-baire-cylinder-namecert-obligations}, and \autoref{thm:real-baire-cylinder-stream-real-handoff} seed the finite Baire-cylinder readback surface for Real-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, host function equality, countable choice, completed Baire branches, selected limits, ambient $\RealUp$ completeness, bridge checking, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, prefix-cylinder stability, StreamName handoff, RegSeqRat readback, Real-seal non-escape, provenance exhaustion, and TasteGate field faithfulness for BEDC.Derived.RealBaireCylinderUp.}
\end{closurestatus}
