\chapter{A Concrete Naming Certificate for $\DyadicCeilingUp$}
\label{ch:concrete-instances-dyadic-ceiling-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\DyadicCeilingUp$ packet records the finite upper-grid endpoint needed when a regular-Cauchy or real-facing read is enclosed from above at a displayed dyadic scale. It sits over the dyadic arithmetic surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the lower-grid dual of \autoref{ch:concrete-instances-dyadicfloor-namecert}, the adjacent endpoint surface of \autoref{ch:concrete-instances-dyadicrounding-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite certificate for the upper endpoint of a dyadic enclosure, not a host ceiling function, order trichotomy decision, quotient real equality, countable-choice selection, chosen representative, ambient $\RealUp$ completeness theorem, or hidden Archimedean search.

\begin{definition}[DyadicCeiling carrier]
\label{def:dyadic-ceiling-carrier}
A $\DyadicCeilingUp$ carrier is a finite $\BHist$ packet
$$
C=(x,k,c,p,\ell,u,M,R,E,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $x$ is the source real-facing request, read only through the regular rational or terminal real rows carried by the packet.
\item $k$ is the requested dyadic scale.
\item $c$ is the $\DyadicRatCoreUp$ grid point claimed as the upper dyadic ceiling row at scale $k$.
\item $p$ is the predecessor row $c-2^{-k}$, recorded as a second $\DyadicRatCoreUp$ row rather than as host integer arithmetic.
\item $\ell$ is the predecessor-lower comparison evidence that the inspected request lies above the predecessor row $p$ at scale $k$.
\item $u$ is the ceiling-upper comparison evidence that the inspected request is bounded above by $c$ at the same scale.
\item $M$ is the $\CauchyModulusUp$ schedule supplying the finite observation threshold needed to read both displayed comparisons.
\item $R$ is the $\RegSeqRatUp$ readback row exposing the regular rational window selected by $M$.
\item $E$ is the terminal $\RealUp$ seal reached only after the dyadic rows and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the request, scale, ceiling row, predecessor row, comparison rows, modulus, readback, seal, continuation, provenance, and local naming rows.
\item $T$ records the displayed $\Cont$ replay from a precision request through $k,c,p,\ell,u,M,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DyadicCeilingUp$, $\DyadicRatCoreUp$, $\DyadicFloorUp$, $\DyadicRoundingUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicCeilingUp}$ row.
\end{enumerate}
The carrier has no coordinate for host ceiling, trichotomy, quotient real equality, countable choice, selected representatives, ambient $\RealUp$ completeness, or hidden Archimedean search.
\end{definition}
\leanchecked{BEDC.Derived.DyadicCeilingUp.TasteGate.DyadicCeilingTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DyadicCeiling NameCert obligations]
\label{thm:dyadic-ceiling-namecert-obligations}
The seed $\NameCert_{\DyadicCeilingUp}$ surface for \autoref{def:dyadic-ceiling-carrier} consists exactly of carrier exposure for $C$, upper-grid exposure through $c$, predecessor exposure through $p$, predecessor-lower comparison through $\ell$, ceiling-upper comparison through $u$, modulus exposure through $M$, regular rational readback through $R$, terminal $\RealUp$ seal exposure through $E$, componentwise transport through $H$, displayed continuation replay through $T$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier tuple $C=(x,k,c,p,\ell,u,M,R,E,H,T,P,N)$. The definition displays every analytic and structural coordinate available to the local naming row.

The upper-grid clauses are finite projections. The row $c$ is the claimed ceiling endpoint, $p$ is its predecessor at the same scale, and the comparison rows $\ell$ and $u$ bind the inspected request between those two dyadic rows.

The remaining coordinates preserve the same packet. The schedule $M$ and readback $R$ supply the finite observation window, the seal $E$ is terminal, and $H,T,P,N$ transport, replay, source, and name the displayed rows. Since the excluded host operations are not coordinates of $C$, the listed rows exhaust the seed obligation surface.
\end{proof}

\begin{theorem}[DyadicCeiling floor-dual route]
\label{thm:dyadic-ceiling-floor-dual-route}
Every accepted $\DyadicCeilingUp$ packet $C=(x,k,c,p,\ell,u,M,R,E,H,T,P,N)$ exposes the upper-grid dual of the $\DyadicFloorUp$ bounding primitive: the predecessor row $p$ and ceiling row $c$ form the finite dyadic interval
$$
p<_k x\leq_k c
$$
at the displayed scale $k$, where $\ell$ reads the predecessor-lower side and $u$ reads the ceiling-upper side. The route factors through
$$
\CauchyModulusUp\longmapsto \RegSeqRatUp\longmapsto \DyadicRatCoreUp\longmapsto \RealUp
$$
and exports no host ceiling, trichotomy branch, quotient real equality, countable-choice row, selected representative, ambient $\RealUp$ completeness, or hidden Archimedean search.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:dyadic-ceiling-carrier}. The only dyadic endpoint rows available at scale $k$ are the predecessor row $p$ and the ceiling row $c$.

Read the two comparison rows next. The row $\ell$ supplies the predecessor-lower evidence, while $u$ supplies the ceiling-upper evidence, so the accepted packet exposes the displayed interval from below by $p$ and from above by $c$.

Finally compare the route with \autoref{ch:concrete-instances-dyadicfloor-namecert}. The floor packet stores a lower grid row and its successor; the ceiling packet stores an upper grid row and its predecessor. Both routes pass through $M,R$ before the dyadic comparison rows and reach $E$ only after the finite regular-rational window has been displayed. Thus the ceiling packet is the upper-grid dual needed for dyadic interval enclosure, without importing any of the excluded ambient operations.
\end{proof}

\falsifiablePrediction{An accepted $\DyadicCeilingUp$ consumer that reads an upper dyadic enclosure without the displayed scale $k$, ceiling row $c$, predecessor row $p$, predecessor-lower evidence $\ell$, ceiling-upper evidence $u$, modulus schedule $M$, and regular readback row $R$ refutes the carrier surface.}

\independenceWitness{dyadicratcore, dyadicfloor, dyadicrounding, regseqrat, real: no listed sibling is bijective to $\DyadicCeilingUp$ because this packet jointly binds a scale, an upper dyadic grid point, its predecessor, two comparison rows, a modulus schedule, regular readback, terminal seal, transport, replay, provenance, and local naming.}

\begin{closurestatus}{\DyadicCeilingUp}
  \constructivestory{A $\DyadicCeilingUp$ packet is generated from a real-facing request, a dyadic scale, an upper dyadic grid point, its predecessor, predecessor-lower and ceiling-upper comparison evidence, a finite modulus schedule, a regular rational readback row, a terminal $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-ceiling-carrier}, \autoref{thm:dyadic-ceiling-namecert-obligations}, and \autoref{thm:dyadic-ceiling-floor-dual-route} seed the finite upper-grid dyadic enclosure primitive for the L10 Real and regular-Cauchy route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host ceiling, trichotomy, quotient real equality, countable choice, selected representatives, ambient $\RealUp$ completeness, hidden Archimedean search, or a Lean theorem.}
  \upgradepath{A formal route can encode the carrier and prove the NameCert obligation surface and floor-dual enclosure theorem for BEDC.Derived.DyadicCeilingUp.}
\end{closurestatus}
