\chapter{A Concrete Naming Certificate for $\BrouwerBarInductionUp$}
\label{ch:concrete-instances-brouwer-bar-induction-namecert}
\origin{human}

Following Brouwer and Troelstra--van Dalen on spreads, bars, and bar induction, the $\BrouwerBarInductionUp$ packet records the finite barred-spread boundary needed by constructive Real and Completion work. It is positioned after the finite fan surface of \autoref{ch:concrete-instances-fantheorem-namecert}, the prefix-law surface of \autoref{ch:concrete-instances-spread-law-namecert}, and the finite choice-sequence surface of \autoref{ch:concrete-instances-choice-sequence-namecert}. Downstream Real and Completion consumers may cite it only through the $\StreamNameUp$ window discipline, the $\RegSeqRatUp$ readback route, and the terminal $\RealUp$ seal; they do not receive countable choice, open-cover compactness, sequential compactness, selected infinite branches, quotient stream equality, or ambient real completeness.

\begin{definition}[Brouwer bar induction carrier]
\label{def:brouwer-bar-induction-carrier}
A $\BrouwerBarInductionUp$ carrier is a finite barred-spread packet
$$
K=(T,B,M,I,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the finite prefix-tree row for the currently inspected spread. It records the displayed root, prefix closure, and finite extension rows, not a completed infinite branch.
\item $B$ is the decidable bar row on prefixes of $T$, including the displayed Bool decisions for every prefix exposed by the current packet.
\item $M$ is the monotone coverage row, asserting that whenever a displayed prefix is barred, every displayed extension remains barred through the same prefix-tree route.
\item $I$ is the induction-step replay row. It records the local backwards step from barred immediate extensions to the displayed parent prefix, using only the finite children visible in $T$.
\item $W$ is the $\StreamNameUp$ window row by which Real and Completion consumers may request finite observations of the spread.
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows when a regular-rational consumer reads the packet.
\item $E$ is the $\RealUp$ handoff row reached only after $T,B,M,I,W,R$ and the structural rows have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the prefix tree, bar decisions, monotone coverage, induction replay, StreamName windows, RegSeqRat readback, Real handoff, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from prefix inspection through bar decisions, monotone closure, induction-step replay, StreamName windows, RegSeqRat readback, and the Real handoff.
\item $P$ is the $\Pkg$ provenance over $\BrouwerBarInductionUp$, $\FanTheoremUp$, $\SpreadLawUp$, $\ChoiceSequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BrouwerBarInductionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $T,B,M,I,W,R,E,H,C,P,N$. It has no coordinate for countable choice, open-cover compactness, sequential compactness, quotient equality of streams, a selected infinite branch, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.BrouwerBarInductionUp.BrouwerBarInductionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Brouwer bar induction prefix stability]
\label{thm:brouwer-bar-induction-prefix-stability}
Let $K=(T,B,M,I,W,R,E,H,C,P,N)$ be an accepted $\BrouwerBarInductionUp$ carrier. Every displayed prefix subtree of $T$, with the restricted bar row, monotone coverage row, induction-step replay row, StreamName windows, RegSeqRat readback, Real handoff, and structural rows inherited from $K$, repacks as an accepted $\BrouwerBarInductionUp$ carrier. The restricted packet has no access to tail values outside the displayed prefix subtree.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:brouwer-bar-induction-carrier}. A displayed prefix subtree is formed by retaining only the prefix rows already present in $T$ together with the corresponding decisions in $B$.

The monotone row $M$ restricts because every retained extension is still an extension inside the original finite tree row. The induction-step row $I$ restricts for the same reason: the local backwards step is read only over the displayed children of the retained parent prefix.

The rows $W,R,E$ remain downstream of the restricted prefix surface. Componentwise transport, continuation replay, provenance, and naming are supplied by $H,C,P,N$, so the restricted tuple is again the same finite packet type and exposes no hidden tail data.
\end{proof}

\begin{theorem}[Brouwer bar induction choice and completeness boundary]
\label{thm:brouwer-bar-induction-choice-boundary}
Every $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, or Completion-facing read of an accepted $\BrouwerBarInductionUp$ carrier factors through
$$
T,B,M,I,W,R,E,H,C,P,N.
$$
The read may use finite barred-prefix information and the displayed induction-step replay, but it cannot extract countable choice, open-cover compactness, sequential compactness without choice-like data, quotient stream equality, a selected infinite branch, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a downstream read. The only analytic-facing rows of the carrier are the StreamName window $W$, the RegSeqRat readback $R$, and the Real handoff $E$.

Replay the continuation row $C$. The route first exposes the prefix tree $T$, the decidable bar row $B$, monotone coverage $M$, and the induction-step row $I$; only then can it open $W$, read $R$, and reach $E$.

The structural rows $H,P,N$ preserve and name that same route. Since the carrier contains no selector for infinite branches, no quotient stream equality row, no open-cover row, no sequential compactness row, and no ambient completeness row, none of those principles can be exported by the packet.
\end{proof}

\begin{theorem}[Brouwer bar induction NameCert obligations]
\label{thm:brouwer-bar-induction-namecert-obligations}
For every accepted $\BrouwerBarInductionUp$ carrier $K=(T,B,M,I,W,R,E,H,C,P,N)$, the local $\NameCert_{\BrouwerBarInductionUp}$ surface consists exactly of the following five finite rows:
\begin{enumerate}
\item carrier admission for the prefix tree, decidable bar, monotone coverage, induction-step replay, StreamName window, RegSeqRat readback, Real handoff, transport, continuation, provenance, and naming rows;
\item prefix stability, requiring every displayed prefix subtree to repack through \autoref{thm:brouwer-bar-induction-prefix-stability};
\item monotone barred-spread replay, requiring bar decisions and extension closure to be read only through $T,B,M$;
\item induction-step exactness, requiring every backwards step to pass through the displayed local replay row $I$ rather than through a host infinite branch;
\item analytic boundary nonescape, requiring every Real or Completion-facing read to use the route of \autoref{thm:brouwer-bar-induction-choice-boundary}.
\end{enumerate}
No local obligation is stored outside these five rows.
\end{theorem}
\begin{proof}
Carrier admission is the tuple displayed in \autoref{def:brouwer-bar-induction-carrier}. The classifier can inspect only the listed coordinates, so the first obligation is exactly the projection of $T,B,M,I,W,R,E,H,C,P,N$.

Prefix stability is \autoref{thm:brouwer-bar-induction-prefix-stability}. It shows that a shorter displayed subtree keeps the same bar, monotone, replay, analytic handoff, transport, continuation, provenance, and naming structure.

The monotone barred-spread and induction-step clauses are read directly from $B,M,I$. The bar row gives only displayed Bool decisions, the monotone row preserves those decisions along displayed extensions, and the replay row supplies only the finite backwards step over visible children.

The analytic boundary is \autoref{thm:brouwer-bar-induction-choice-boundary}. It forces every StreamName, RegSeqRat, Real, or Completion consumer through $W,R,E$ after the barred-spread rows have been displayed.

The packet has no further coordinate. Therefore countable choice, open-cover compactness, sequential compactness, quotient stream equality, selected infinite branches, and ambient $\RealUp$ completeness are not local NameCert obligations.
\end{proof}

\falsifiablePrediction{Every accepted $\BrouwerBarInductionUp$ Real or Completion-facing read factors through a displayed finite prefix tree, decidable bar row, monotone coverage row, induction-step replay row, StreamName window, RegSeqRat readback, Real handoff, transport, continuation, provenance, and local naming.}

\independenceWitness{fantheorem, spread-law, choice-sequence, streamname, regseqrat, real: $\BrouwerBarInductionUp$ is not bijective to any listed sibling because it jointly carries a finite barred-spread prefix tree, decidable bar, monotone coverage, induction-step replay, analytic window handoff, transport, continuation, provenance, and local naming while refusing branch selection and ambient completeness.}

\closureat{BrouwerBarInductionUp}{seedStr}

\begin{closurestatus}{\BrouwerBarInductionUp}
  \constructivestory{A $\BrouwerBarInductionUp$ packet is generated from a finite prefix tree, a decidable bar row, monotone coverage, induction-step replay, StreamName windows, RegSeqRat readback, a Real handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:brouwer-bar-induction-carrier}, \autoref{thm:brouwer-bar-induction-prefix-stability}, \autoref{thm:brouwer-bar-induction-choice-boundary}, and \autoref{thm:brouwer-bar-induction-namecert-obligations} seed the finite barred-spread boundary for Real and Completion-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, open-cover compactness, sequential compactness, quotient stream equality, selected infinite branches, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, prefix stability, monotone barred-spread replay, induction-step exactness, analytic boundary nonescape, and TasteGate field faithfulness for BEDC.Derived.BrouwerBarInductionUp.}
\end{closurestatus}
