\chapter{A Concrete Naming Certificate for $\EffectiveCauchySequenceUp$}
\label{ch:concrete-instances-effective-cauchy-sequence-namecert}
\origin{human}

Following Bishop and Bridges, the $\EffectiveCauchySequenceUp$ packet records a Cauchy sequence whose convergence is exposed by an explicit modulus before any $\RegSeqRatUp$ handoff or terminal $\RealUp$ seal is read. It sits on the finite-window route of \autoref{ch:concrete-instances-streamname-namecert}, the modulus schedule surface of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a source-level certificate for explicit-modulus Cauchy sequence data on the current Real and Completion route; it is not quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Effective Cauchy sequence carrier]\label{def:effective-cauchy-sequence-carrier}
An $\EffectiveCauchySequenceUp$ carrier is a finite $\BHist$ packet
$$
G=(S,M,W,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the sequence source row. It names the displayed source of observations whose finite windows are inspected by Real-facing or Completion-facing consumers.
\item $M$ is the explicit $\CauchyModulusUp$ row. For each requested positive tolerance it gives the finite stage after which the source row is to be read within that tolerance.
\item $W$ is the finite $\StreamNameUp$ window row. It records the actual inspected source windows downstream of the modulus schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It stores the dyadic radii, slack rows, comparison budgets, and tolerance conversions used by $M$ and $W$.
\item $Q$ is the $\RegSeqRatUp$ handoff row. It records the regular rational readback obtained only after the source, modulus, window, and dyadic ledger rows have been displayed.
\item $E$ is the terminal $\RealUp$ seal row reached downstream of $S,M,W,D,Q$.
\item $H$ records componentwise $\hsame$ transport for the source, modulus, window, dyadic ledger, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Real or Completion request through $S,M,W,D,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\EffectiveCauchySequenceUp$, $\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\EffectiveCauchySequenceUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite explicit-modulus Cauchy sequence packet. It has no coordinate for quotient stream equality, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.EffectiveCauchySequenceUp.TasteGate.EffectiveCauchySequenceUpTasteGate\_single\_carrier\_alignment}
\leanchecked{BEDC.Derived.EffectiveCauchySequenceUp.EffectiveCauchySequenceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Effective Cauchy sequence NameCert obligations]\label{thm:effective-cauchy-sequence-namecert-obligations}
For every accepted $\EffectiveCauchySequenceUp$ carrier $G=(S,M,W,D,Q,E,H,C,P,N)$, the local $\NameCert_{\EffectiveCauchySequenceUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the displayed sequence source, explicit modulus, finite stream windows, dyadic tolerance ledger, regular rational handoff, Real seal, transport, replay, provenance, and local naming rows;
\item modulus exposure, requiring every tolerance request to read $M$ before the corresponding window row $W$ is consumed;
\item dyadic tolerance accounting, requiring every use of the modulus to pass through the dyadic radii, slack rows, comparison budgets, and tolerance conversions stored in $D$;
\item regular readback, requiring $Q$ to be downstream of the source, modulus, window, and dyadic rows before any regular rational observation is exported;
\item Real seal boundary, requiring $E$ to remain downstream of $S,M,W,D,Q$ and never to serve as quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, or ambient completeness;
\item transport, replay, provenance, and local naming stability, requiring $H,C,P,N$ to preserve and name exactly the displayed packet.
\end{enumerate}
No effective-Cauchy-sequence obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is the projection of \autoref{def:effective-cauchy-sequence-carrier}. The projected rows are exactly the sequence source $S$, explicit modulus $M$, finite windows $W$, dyadic ledger $D$, regular readback $Q$, Real seal $E$, and structural rows $H,C,P,N$.

Modulus exposure reads \autoref{ch:concrete-instances-cauchymodulus-namecert} together with the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}. A tolerance request cannot reach the inspected window row $W$ until the corresponding stage has first been supplied by $M$.

Dyadic tolerance accounting is supplied by \autoref{ch:concrete-instances-dyadicratcore-namecert}. The row $D$ is the only displayed place where radii, slack, comparison budgets, and tolerance conversions live, so every modulus-guided read must pass through it before reaching the regular readback.

The regular readback and Real boundary then follow the route of \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}. Since $Q$ and $E$ are downstream of $S,M,W,D$, neither row can introduce a quotient stream, selected limit, countable choice, trichotomy, host real equality, or ambient completeness datum.

Finally, $H,C,P,N$ transport, replay, package, and name the same displayed rows. They add no analytic coordinate beyond the carrier, so the six listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Effective Cauchy sequence RegSeqRat handoff]\label{thm:effective-cauchy-sequence-regseqrat-handoff}
Every $\RegSeqRatUp$ read exported by an accepted $\EffectiveCauchySequenceUp$ carrier $G=(S,M,W,D,Q,E,H,C,P,N)$ factors through the finite route
$$
S \longmapsto M \longmapsto W \longmapsto D \longmapsto Q \longmapsto H,C,P,N .
$$
Thus a regular rational consumer receives the displayed source, explicit modulus, finite stream windows, dyadic tolerance ledger, regular readback, transport, replay, provenance, and local naming before it can inspect the handoff.
\end{theorem}
\begin{proof}
Begin with a $\RegSeqRatUp$ read of $G$. By \autoref{def:effective-cauchy-sequence-carrier}, the only regular readback coordinate is $Q$, and $Q$ is placed after the source, modulus, window, and dyadic ledger rows.

The first part of the route reads $S$ through the window interface of \autoref{ch:concrete-instances-streamname-namecert}. The explicit stage discipline is then supplied by $M$ through \autoref{ch:concrete-instances-cauchymodulus-namecert}, and the inspected finite windows are recorded by $W$.

The tolerance conversion and comparison work is read through $D$ using \autoref{ch:concrete-instances-dyadicratcore-namecert}. Only after that dyadic ledger is fixed does \autoref{ch:concrete-instances-regseqrat-namecert} expose the regular rational handoff $Q$.

The rows $H,C,P,N$ preserve and name the same order. Therefore every regular rational read factors through the displayed route and has no bypass through quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[Effective Cauchy sequence Real seal boundary]\label{thm:effective-cauchy-sequence-real-seal-boundary}
Every $\RealUp$-facing read of an accepted $\EffectiveCauchySequenceUp$ carrier $G=(S,M,W,D,Q,E,H,C,P,N)$ factors through
$$
S \longmapsto M \longmapsto W \longmapsto D \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Consequently the terminal Real seal is available only after the source, explicit modulus, finite windows, dyadic tolerance ledger, and regular rational handoff have been displayed.
\end{theorem}
\begin{proof}
Start from a $\RealUp$-facing consumer. The carrier definition exposes the terminal seal only as the row $E$ in the same finite packet as $S,M,W,D,Q,H,C,P,N$.

Replay the continuation row $C$. The consumer first reads the source row $S$, obtains the requested stage from the explicit modulus $M$, inspects the finite stream windows $W$, and checks the dyadic tolerance ledger $D$ before any regular rational handoff can be consumed.

The regular readback $Q$ then supplies the only route into the terminal seal of \autoref{ch:concrete-instances-real-namecert}. Since $E$ is downstream of $Q$, the Real-facing read cannot export quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, or an ambient completeness theorem for $\RealUp$.

Componentwise transport, replay, provenance, and local naming preserve the route. Hence every Real-facing read factors through the displayed source-to-seal boundary.
\end{proof}

\begin{theorem}[Effective Cauchy sequence non-escape]\label{thm:effective-cauchy-sequence-nonescape}
Let $G=(S,M,W,D,Q,E,H,C,P,N)$ be an accepted $\EffectiveCauchySequenceUp$ carrier. No consumer of $G$ can read quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking from the packet unless that datum is already one of the displayed rows $S,M,W,D,Q,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Inspect the carrier rows in \autoref{def:effective-cauchy-sequence-carrier}. The analytic rows are only the source, explicit modulus, finite windows, dyadic ledger, regular readback, and terminal Real seal.

The structural rows $H,C,P,N$ provide sameness transport, replay, provenance, and local naming for those same rows. They do not add a quotient relation, limit selector, choice principle, order decision, host equality predicate, completeness theorem, Lean target, or bridge certificate.

Therefore the excluded data have no carrier coordinate, replay edge, provenance entry, or local NameCert row from which to be read. Any consumer of $G$ is confined to the displayed explicit-modulus route.
\end{proof}

\falsifiablePrediction{Every $\EffectiveCauchySequenceUp$ regular or Real-facing read factors through a sequence source row, explicit CauchyModulus row, finite StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat handoff, RealUp seal, transport, replay, provenance, and local naming.}

\independenceWitness{streamname, cauchymodulus, dyadicratcore, regseqrat, real: $\EffectiveCauchySequenceUp$ is not bijective to any listed sibling because it jointly carries a source row, explicit modulus, finite windows, tolerance ledger, regular handoff, Real seal, transport, replay, provenance, and local naming.}

\closureat{EffectiveCauchySequenceUp}{seedStr}
\begin{closurestatus}{\EffectiveCauchySequenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:effective-cauchy-sequence-carrier}, \autoref{thm:effective-cauchy-sequence-namecert-obligations}, \autoref{thm:effective-cauchy-sequence-regseqrat-handoff}, \autoref{thm:effective-cauchy-sequence-real-seal-boundary}, and \autoref{thm:effective-cauchy-sequence-nonescape} seed the finite explicit-modulus Cauchy sequence route through $\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus exposure, dyadic tolerance accounting, regular readback, Real seal boundary, transport, replay, provenance, local naming, and non-escape for BEDC.Derived.EffectiveCauchySequenceUp.}
  \constructivestory{An $\EffectiveCauchySequenceUp$ packet is generated from a displayed sequence source, explicit $\CauchyModulusUp$ row, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ handoff, terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
