\chapter{A Concrete Naming Certificate for $\MarkovPrincipleBoundaryUp$}
\label{ch:concrete-instances-markov-principle-boundary-namecert}
\origin{human}

Following Markov, Ishihara, and Bishop--Bridges constructive analysis, the $\MarkovPrincipleBoundaryUp$ packet records the finite boundary at which an inspection argument may use Markov-style negative evidence as named data without accepting Markov's principle as a global rule. It is read beside the Ishihara inspection packet of \autoref{ch:concrete-instances-ishihara-trick-namecert}, the Specker control example of \autoref{ch:concrete-instances-speckersequence-namecert}, the stream schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a Real/Completion boundary object: it exposes only the finite rows a consumer may inspect and refuses any route that would turn those rows into LPO, LLPO, trichotomy, countable choice, quotient stream equality, selected limits, or ambient real completeness.

\begin{definition}[Markov principle boundary carrier]
\label{def:markov-principle-boundary-carrier}
A $\MarkovPrincipleBoundaryUp$ carrier is a finite $\BHist$ packet
$$
M=(I,K,S,R,D,E,W,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $I$ is an $\IshiharaTrickUp$ inspection row naming the finite apartness/refinement test whose branch is being bounded.
\item $K$ is a $\SpeckerSequenceUp$ control row recording the nonconvergent obstruction that prevents the inspection from becoming a selected real limit.
\item $S$ is a $\StreamNameUp$ schedule row listing the finite stream requests admitted by the boundary.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational values actually inspected from $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger naming the radii, endpoint comparisons, and finite margin rows used by the boundary.
\item $E$ is the $\RealUp$ seal reached only after the rows $I,K,S,R,D$ have been displayed.
\item $W$ is the Markov-boundary witness row: it records either a displayed finite failure of zerohood in the inspected schedule or the finite refusal row explaining why no global Markov rule is exported.
\item $H$ stores componentwise $\hsame$ transport for the inspection, Specker control, schedule, readback, dyadic ledger, real seal, witness row, provenance, and local name.
\item $C$ stores $\Cont$ replay from finite schedule requests through $R$ and $D$, through the Ishihara branch $I$, and finally into the sealed real-facing witness $W$.
\item $P$ records $\Pkg$ provenance over $\MarkovPrincipleBoundaryUp$, $\IshiharaTrickUp$, $\SpeckerSequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MarkovPrincipleBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for Markov's principle as an imported axiom, LPO, LLPO, trichotomy, countable choice, quotient stream equality, selected limits, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.MarkovPrincipleBoundaryUp.MarkovPrincipleBoundaryUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Ishihara--Specker boundary route]
\label{thm:markov-principle-boundary-ishihara-specker-route}
For every accepted $\MarkovPrincipleBoundaryUp$ carrier $M=(I,K,S,R,D,E,W,H,C,P,N)$, every real-facing inspection branch factors through the displayed route
$$
I,K,S,R,D,E,W,H,C,P,N.
$$
Consequently an $\IshiharaTrickUp$ refinement may be compared with a $\SpeckerSequenceUp$ obstruction only by citing the finite stream schedule, regular-rational readback, dyadic tolerance ledger, real seal, witness row, componentwise transport, replay, provenance, and local NameCert row displayed by $M$.
\end{theorem}
\begin{proof}
The carrier definition lists the only coordinates admitted by the boundary. The Ishihara inspection row $I$ supplies the finite branch being tested, while the Specker row $K$ supplies the obstruction preventing that branch from being promoted to a selected limit.

The schedule-readback-tolerance part is carried by $S,R,D$. Thus every inspected rational value and every finite margin used by the branch is named before the real seal $E$ is reached.

The witness row $W$ is downstream of those finite rows. Componentwise $\hsame$ transport in $H$ and $\Cont$ replay in $C$ allow a consumer to replay the route without adding any unlisted classifier. The provenance and local NameCert rows $P,N$ then repack the same displayed data as the public boundary certificate.
\end{proof}

\begin{theorem}[Markov boundary nonescape]
\label{thm:markov-principle-boundary-nonescape}
Every Real/Completion consumer of an accepted $\MarkovPrincipleBoundaryUp$ packet receives only finite inspection data and the sealed witness row $W$. It receives no Markov's principle as an imported axiom, no LPO, no LLPO, no trichotomy, no countable choice, no quotient stream equality, no selected limit, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Let a Real/Completion consumer accept $M=(I,K,S,R,D,E,W,H,C,P,N)$. By \autoref{def:markov-principle-boundary-carrier}, the only real-facing coordinate is the seal $E$, and the only Markov-sensitive coordinate is the displayed witness row $W$.

The route theorem \autoref{thm:markov-principle-boundary-ishihara-specker-route} forces the consumer to reach $W$ through the finite Ishihara inspection, Specker control, stream schedule, regular-rational readback, and dyadic tolerance ledger. None of these coordinates contains a global principle or a selected completion operator.

Since the carrier has no coordinate for Markov's principle as an imported axiom, LPO, LLPO, trichotomy, countable choice, quotient stream equality, selected limits, or ambient real completeness, transport and replay cannot export any such principle through the local $\NameCert_{\MarkovPrincipleBoundaryUp}$ row.
\end{proof}

\closureat{MarkovPrincipleBoundaryUp}{seedStr}

\begin{closurestatus}{\MarkovPrincipleBoundaryUp}
  \constructivestory{A $\MarkovPrincipleBoundaryUp$ packet is generated from an Ishihara inspection row, Specker control row, StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, Markov-boundary witness row, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:markov-principle-boundary-carrier}, \autoref{thm:markov-principle-boundary-ishihara-specker-route}, and \autoref{thm:markov-principle-boundary-nonescape} seed the finite Real/Completion boundary for Markov-sensitive inspection.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.MarkovPrincipleBoundaryUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Markov's principle as an imported axiom, LPO, LLPO, trichotomy, countable choice, quotient stream equality, selected limits, ambient real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Ishihara--Specker route factorization, stream-readback tolerance discipline, real-boundary handoff, componentwise transport and replay stability, and ledger nonescape for the same finite packet.}
\end{closurestatus}
