\chapter{A Concrete Naming Certificate for $\BishopFanModulusUp$}
\label{ch:concrete-instances-bishop-fan-modulus-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and Troelstra--van Dalen's treatment of fan bars, the $\BishopFanModulusUp$ packet records the finite route by which a barred fan depth ledger becomes an explicit Real and Completion window modulus. It sits after the finite fan certificate of \autoref{ch:concrete-instances-fantheorem-namecert}, the Cantor-space naming surface of \autoref{ch:concrete-instances-cantorspace-namecert}, the StreamName window interface of \autoref{ch:concrete-instances-streamname-namecert}, the RegSeqRat readback boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, the DyadicRatCore tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Real seal of \autoref{ch:concrete-instances-real-namecert}, and the downstream uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet is a finite modulus bridge for L10 Real and Completion routes; it is not open-cover compactness, countable choice, a selected branch, a selected limit, quotient stream equality, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop fan modulus carrier]
\label{def:bishop-fan-modulus-carrier}
A $\BishopFanModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(F,A,B,S,Q,D,R,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FanTheoremUp$ finite fan row. It records the displayed binary fan, prefix closure, decidable branch-prefix inspection, and the finite bar-depth bound.
\item $A$ is the $\CantorSpaceUp$ address row. It names the finite binary-prefix domain on which the fan row is read, without selecting an infinite branch.
\item $B$ is the bar-to-modulus row. For each displayed bar depth from $F$, it records the finite observation depth that bounds all branch-prefix reads used by the Real or Completion consumer.
\item $S$ is the $\StreamNameUp$ window row. It records exactly the source windows inspected after the bar-to-modulus row has fixed the required depth.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from those windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row. It stores dyadic radii, comparison budgets, and refinement slack attached to the same window schedule.
\item $R$ is the terminal $\RealUp$ seal row reached only after $F,A,B,S,Q,D$ have been displayed.
\item $U$ is the $\UniformModulusUp$ consumer row. It exposes the same depth schedule as an explicit modulus for later uniform, Real, and Completion-facing routes.
\item $H$ records componentwise $\hsame$ transport for the fan, Cantor-address, bar-to-modulus, stream-window, regular-readback, dyadic-tolerance, Real-seal, uniform-modulus, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a consumer request through $F,A,B,S,Q,D,R,U,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopFanModulusUp$, $\FanTheoremUp$, $\CantorSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopFanModulusUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,A,B,S,Q,D,R,U,H,C,P,N$. It has no coordinate for open-cover compactness, countable choice, selected infinite branches, selected limits, quotient stream equality, host real equality, Lean verification, bridge checking, or ambient $\RealUp$ completeness.
\leandef{BEDC.Derived.BishopFanModulusUp.TasteGate.BishopFanModulusUp}
\leanchecked{BEDC.Derived.BishopFanModulusUp.TasteGate.BishopFanModulusTasteGate\_single\_carrier\_alignment}
\end{definition}

\begin{theorem}[Bishop fan modulus NameCert obligations]
\label{thm:bishop-fan-modulus-namecert-obligations}
For every accepted $\BishopFanModulusUp$ carrier $M=(F,A,B,S,Q,D,R,U,H,C,P,N)$, the local $\NameCert_{\BishopFanModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed fan, Cantor-address, bar-to-modulus, stream-window, regular-readback, dyadic-tolerance, Real-seal, uniform-modulus, transport, replay, provenance, and local naming rows;
\item fan-bar coverage, requiring every branch-prefix request to be bounded by the finite bar-depth row read from $F$ over the address surface $A$;
\item modulus extraction, requiring the depth row $B$ to convert that finite bar-depth data into the window depth consumed by $S$ and $U$;
\item Real window handoff, requiring every $\StreamNameUp$ window to pass through $S$, every regular readback to pass through $Q$, every dyadic tolerance check to pass through $D$, and every terminal real read to pass through $R$;
\item uniform-modulus handoff, requiring $U$ to expose only the same finite schedule already displayed by $F,A,B,S,Q,D,R$;
\item transport, replay, provenance, and local naming stability, requiring $H,C,P,N$ to preserve and name exactly the displayed packet.
\end{enumerate}
No Bishop fan modulus obligation is stored outside these six rows.
\end{theorem}
\leanchecked{BEDC.Derived.BishopFanModulusUp.BishopFanModulusUpTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:bishop-fan-modulus-carrier}. The projected finite packet is exactly $F,A,B,S,Q,D,R,U,H,C,P,N$.

Fan-bar coverage reads the finite fan row and the Cantor-address row together. The bar depth is supplied by $F$, and the binary-prefix domain on which it is interpreted is supplied by $A$, so the argument ranges only over displayed finite prefixes.

The modulus row $B$ converts this bar depth into a window schedule. Once $B$ has fixed the depth, the stream row $S$ can expose finite observations and the uniform row $U$ can expose the same schedule as a $\UniformModulusUp$ consumer surface.

The Real-facing route then passes through $Q,D,R$. Regular readback is read from $Q$, dyadic tolerance accounting is read from $D$, and the terminal $\RealUp$ seal is read from $R$ only after the window schedule has already been displayed.

Finally, $H,C,P,N$ transport, replay, record, and name the same route. Since the carrier contains no further coordinate, the excluded compactness, choice, branch-selection, limit-selection, quotient, host-equality, verification, bridge, and ambient-completeness data cannot be exported.
\end{proof}

\begin{theorem}[Bishop fan modulus Real window handoff]
\label{thm:bishop-fan-modulus-real-window-handoff}
Every $\RealUp$ or Completion-facing read of an accepted $\BishopFanModulusUp$ carrier $M=(F,A,B,S,Q,D,R,U,H,C,P,N)$ factors through
$$
F \longmapsto A \longmapsto B \longmapsto S \longmapsto Q \longmapsto D \longmapsto R \longmapsto U \longmapsto H,C,P,N .
$$
Thus the consumer receives a finite fan-bar depth, a Cantor-prefix address surface, an explicit window schedule, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance data, a Real seal, a UniformModulus handoff, and the structural support rows before it can inspect the Real or Completion boundary.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$ or Completion-facing request. By \autoref{def:bishop-fan-modulus-carrier}, the request can reach the terminal Real row $R$ only through the displayed packet.

The route first reads $F$ and $A$. These two rows fix the finite fan surface and the finite Cantor-prefix domain, so the bar-depth request has no access to a selected infinite branch.

The row $B$ then turns the finite bar-depth data into the observation depth consumed by $S$. The regular readback $Q$ and dyadic tolerance row $D$ are downstream of that same window schedule.

Only after $S,Q,D$ are displayed can the Real seal $R$ and the uniform-modulus row $U$ be read. The rows $H,C,P,N$ preserve the same order as transport, continuation, provenance, and local naming data.

Therefore every Real or Completion-facing consumer factors through the displayed finite route. The carrier has no bypass through open-cover compactness, countable choice, selected branches, selected limits, quotient stream equality, host real equality, or ambient Real completeness.
\end{proof}

\begin{theorem}[Bishop fan modulus non-escape]
\label{thm:bishop-fan-modulus-nonescape}
Let $M=(F,A,B,S,Q,D,R,U,H,C,P,N)$ be an accepted $\BishopFanModulusUp$ carrier. No consumer of $M$ can read open-cover compactness, countable choice, a selected infinite branch, a selected limit, quotient stream equality, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking from the packet unless that datum is already one of the displayed rows $F,A,B,S,Q,D,R,U,H,C,P,N$.
\end{theorem}
\begin{proof}
Inspect the accepted carrier. Its analytic coordinates are the fan row $F$, Cantor-address row $A$, bar-to-modulus row $B$, StreamName window row $S$, RegSeqRat readback row $Q$, DyadicRatCore tolerance row $D$, Real seal row $R$, and UniformModulus row $U$.

The remaining coordinates $H,C,P,N$ provide componentwise sameness transport, displayed continuation replay, package provenance, and local naming for those same rows. They do not add a compactness object, choice principle, branch selector, limit selector, quotient relation, host equality predicate, completeness theorem, Lean target, or bridge certificate.

Thus the excluded data have no carrier coordinate, continuation edge, provenance entry, or local NameCert row from which to be read. Every consumer is confined to the displayed fan-bar-to-window-modulus route.
\end{proof}

\falsifiablePrediction{Every $\BishopFanModulusUp$ Real or Completion-facing read factors through a finite fan row, Cantor-prefix address row, bar-to-modulus row, StreamName window, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, UniformModulus handoff, transport, replay, provenance, and local naming.}

\independenceWitness{fantheorem, cantorspace, streamname, regseqrat, dyadicratcore, real, uniformmodulus: $\BishopFanModulusUp$ is not bijective to any listed sibling because it jointly carries fan-bar depth, Cantor-prefix addressing, explicit window scheduling, analytic readback rows, a Real seal, a UniformModulus handoff, and structural support while refusing compactness, choice, branch selection, selected limits, quotient stream equality, host equality, and ambient completeness.}

\closureat{BishopFanModulusUp}{seedStr}
\begin{closurestatus}{\BishopFanModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-fan-modulus-carrier}, \autoref{thm:bishop-fan-modulus-namecert-obligations}, \autoref{thm:bishop-fan-modulus-real-window-handoff}, and \autoref{thm:bishop-fan-modulus-nonescape} seed the finite fan-bar-to-window-modulus route through $\FanTheoremUp$, $\CantorSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\UniformModulusUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, countable choice, selected branches, selected limits, quotient stream equality, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, fan-bar coverage, modulus extraction, Real window handoff, uniform-modulus handoff, transport, replay, provenance, local naming, and non-escape for BEDC.Derived.BishopFanModulusUp.}
  \constructivestory{A $\BishopFanModulusUp$ packet is generated from a finite $\FanTheoremUp$ row, $\CantorSpaceUp$ address row, bar-to-modulus row, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, $\RealUp$ seal, $\UniformModulusUp$ handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
