\chapter{A Concrete Naming Certificate for $\RegularCauchyDivisionUp$}
\label{ch:concrete-instances-regular-cauchy-division-namecert}
\origin{human}

Bishop and Bridges constructive analysis treats division of regular real names as multiplication by a reciprocal, with a displayed nonzero witness for the denominator before any reciprocal estimate is consumed. The $\RegularCauchyDivisionUp$ packet records that finite surface for regular Cauchy rational names: a numerator source, a denominator source with apartness evidence, the sibling reciprocal certificate, the sibling product certificate, a tolerance ledger, and the terminal $\RealUp$ seal route. It composes the surfaces of \autoref{ch:concrete-instances-regular-cauchy-reciprocal-namecert} and \autoref{ch:concrete-instances-regularcauchyproduct-namecert} beside the additive siblings \autoref{ch:concrete-instances-regularcauchydifference-namecert} and \autoref{ch:concrete-instances-regularcauchysum-namecert}. The packet exposes no quotient stream, selected host limit, trichotomy decision, or ambient real completeness principle.

\begin{definition}[Regular Cauchy division carrier]
\label{def:regular-cauchy-division-carrier}
A $\RegularCauchyDivisionUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
V=(N,D,A,R,P,L,S,H,C,G,M)
$$
with the following displayed rows:
\begin{enumerate}
\item $N$ is the numerator $\RegSeqRatUp$ source row whose scheduled rational observations supply the left input.
\item $D$ is the denominator $\RegSeqRatUp$ source row whose scheduled rational observations supply the right input.
\item $A$ is the denominator apartness and nonzero-witness row, displayed before any reciprocal read of $D$.
\item $R$ is the $\RegularCauchyReciprocalUp$ row whose source is $D$ and whose apartness input is $A$.
\item $P$ is the $\RegularCauchyProductUp$ row whose two sources are $N$ and the regular readback exported by $R$.
\item $L$ is the finite tolerance ledger recording the numerator tolerance, denominator apartness margin, reciprocal budget, product-error budget, and the output tolerance assigned to the division readback.
\item $S$ is the $\RealUp$ seal row reached only after the numerator source, denominator source, apartness row, reciprocal row, product row, and ledger row have been consumed.
\item $H$ records componentwise $\hsame$ transport for $N,D,A,R,P,L,S,C,G,M$.
\item $C$ records the displayed $\Cont$ replay for numerator inspection, denominator inspection, apartness exposure, reciprocal handoff, product handoff, finite-ledger exposure, and Real seal handoff.
\item $G$ is the $\Pkg$ provenance over $\RegSeqRatUp$, $\StreamNameUp$, $\RegularCauchyReciprocalUp$, $\RegularCauchyProductUp$, $\FiniteErrorBudgetUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$.
\item $M$ is the local $\NameCert_{\RegularCauchyDivisionUp}$ row.
\end{enumerate}
The local classifier compares accepted division carriers only through the displayed rows $N,D,A,R,P,L,S,H,C,G,M$.
\end{definition}

\begin{theorem}[Regular Cauchy division NameCert obligations]
\label{thm:regular-cauchy-division-namecert-obligations}
The seed $\NameCert_{\RegularCauchyDivisionUp}$ surface for the carrier of \autoref{def:regular-cauchy-division-carrier} consists exactly of carrier admission, denominator apartness exposure, reciprocal-source handoff, product-source handoff, finite tolerance-ledger exposure, $\RealUp$ seal exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming for $M$.
\end{theorem}
\begin{proof}
Carrier admission is projection from the tuple in \autoref{def:regular-cauchy-division-carrier}. The numerator row $N$, denominator row $D$, apartness row $A$, reciprocal row $R$, product row $P$, ledger row $L$, seal row $S$, transport row $H$, replay row $C$, provenance row $G$, and local naming row $M$ are all explicit coordinates.

The analytic rows are ordered by the two sibling surfaces. The denominator apartness row $A$ must be visible before the reciprocal row $R$ can be read, and the product row $P$ reads only after the numerator row $N$ and the reciprocal readback supplied by $R$ are visible.

The structural rows transport and replay that same finite route. Since neither $H$ nor $C$ adds a quotient stream, selected limit, trichotomy decision, host real equality, or ambient completeness theorem, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Regular Cauchy division reciprocal-product handoff]
\label{thm:regular-cauchy-division-reciprocal-product-handoff}
For every accepted $\RegularCauchyDivisionUp$ carrier $V=(N,D,A,R,P,L,S,H,C,G,M)$, every $\RegSeqRatUp$ read of the division result factors through
$$
(N,D,A)\longmapsto R\longmapsto P\longmapsto L.
$$
The route first reads the denominator apartness witness, then the $\RegularCauchyReciprocalUp$ row for $D$, then the $\RegularCauchyProductUp$ row combining $N$ with the reciprocal readback, and finally the finite tolerance ledger $L$.
\end{theorem}
\begin{proof}
Start with the denominator side. The reciprocal sibling \autoref{ch:concrete-instances-regular-cauchy-reciprocal-namecert} exposes a reciprocal readback only after the denominator $\RegSeqRatUp$ source and its apartness witness have been displayed.

Next pass the reciprocal readback to the product sibling. The product surface of \autoref{ch:concrete-instances-regularcauchyproduct-namecert} consumes two regular sources, so in this packet those sources are the numerator row $N$ and the readback exported by $R$.

Finally read the ledger row $L$. It records the tolerance data inherited from the numerator source, the denominator apartness margin, the reciprocal budget, and the product-error budget before any downstream regular read is exposed. Thus the handoff is the finite reciprocal-product route and not a quotient or selected-limit construction.
\end{proof}

\begin{theorem}[Regular Cauchy division RealUp seal boundary]
\label{thm:regular-cauchy-division-real-seal-boundary}
Any $\RealUp$ consumer of an accepted $\RegularCauchyDivisionUp$ packet reads only the finite reciprocal-product route listed in \autoref{thm:regular-cauchy-division-reciprocal-product-handoff}, together with the visible $\hsame$ transports, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\RegularCauchyDivisionUp}$ row.
\end{theorem}
\begin{proof}
Factor the real-facing read through the regular readback supplied by the product row $P$. By \autoref{thm:regular-cauchy-division-reciprocal-product-handoff}, that product row is already downstream of the numerator source, denominator source, apartness witness, reciprocal row, and finite ledger.

The remaining rows visible to a real consumer are structural. The $\hsame$ row transports the same listed coordinates, the $\Cont$ row replays the same finite route, the $\Pkg$ row records provenance, and the local $\NameCert$ row names the packet.

The carrier has no independent completed-real quotient coordinate and no hidden equality field. Therefore the $\RealUp$ seal boundary can consume only the displayed reciprocal-product packet and its visible provenance.
\end{proof}

\falsifiablePrediction{An accepted $\RegularCauchyDivisionUp$ consumer that reaches a division readback or a $\RealUp$ seal without the displayed numerator $\RegSeqRatUp$ source, denominator $\RegSeqRatUp$ source, apartness witness, $\RegularCauchyReciprocalUp$ row, $\RegularCauchyProductUp$ row, and finite tolerance ledger refutes the carrier surface.}

\independenceWitness{regular-cauchy-reciprocal, regular-cauchy-product, regular-cauchy-difference, regular-cauchy-sum, regseqrat, streamname, real: no listed sibling supplies the whole eleven-row packet $V=(N,D,A,R,P,L,S,H,C,G,M)$, because the reciprocal sibling supplies only denominator inversion data, the product sibling supplies only two-source multiplication data, the additive siblings supply no denominator apartness route, and the regular-name and Real seal siblings supply only the source or terminal faces.}

\begin{closurestatus}{\RegularCauchyDivisionUp}
  \constructivestory{A $\RegularCauchyDivisionUp$ packet is generated from numerator and denominator $\RegSeqRatUp$ sources, a denominator apartness witness, a $\RegularCauchyReciprocalUp$ row, a $\RegularCauchyProductUp$ row, a finite tolerance ledger, a terminal $\RealUp$ seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-division-carrier}, \autoref{thm:regular-cauchy-division-namecert-obligations}, \autoref{thm:regular-cauchy-division-reciprocal-product-handoff}, and \autoref{thm:regular-cauchy-division-real-seal-boundary} seed the finite reciprocal-product division surface for regular Cauchy names over $\RegSeqRatUp$, $\StreamNameUp$, $\RegularCauchyReciprocalUp$, $\RegularCauchyProductUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient streams, selected limits, trichotomy, a total reciprocal, host real division, ambient real completeness, or a Lean theorem.}
  \upgradepath{A formal route can encode the eleven-row carrier and prove the NameCert-obligation, reciprocal-product handoff, and Real seal-boundary theorems.}
\end{closurestatus}
