\chapter{A Concrete Naming Certificate for $\RegularCauchyApartnessOrderUp$}
\label{ch:concrete-instances-regular-cauchy-apartness-order-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\RegularCauchyApartnessOrderUp$ packet records the positive comparison and apartness reads available from regular Cauchy real names before any trichotomy, quotient-real equality, selected representative, or ambient completeness principle is admitted. It sits after the finite budget route of \autoref{ch:concrete-instances-regular-cauchy-apartness-budget-namecert}, the comparison boundary of \autoref{ch:concrete-instances-bishoprealcomparison-namecert}, and the positive-gap interface of \autoref{ch:concrete-instances-apartnessspace-namecert}. Its public role is an L10 constructive order/apartness boundary over displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows.

\begin{definition}[Regular Cauchy apartness-order carrier]
\label{def:regular-cauchy-apartness-order-carrier}
A $\RegularCauchyApartnessOrderUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,A,O,M,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the accepted $\RegSeqRatUp$ source whose regular rational observations supply the two comparison endpoints or the single signed difference stream under inspection.
\item $A$ is the $\RegularCauchyApartnessBudgetUp$ row. It records the finite positive lower-bound budget that must be displayed before any strict comparison or apartness read is exported.
\item $O$ is the comparison-direction row. It records whether the packet is being read as positive apartness, $<$, $>$, or a one-sided order read, and it stores only the displayed direction tag and its local classifier data.
\item $M$ is the modulus row selecting the finite precision at which the budgeted positive separation is inspected.
\item $W$ is the $\StreamNameUp$ window row selected from $X$ by $A,M$, and $O$.
\item $D$ is the $\DyadicRatCoreUp$ positive-bound readback row obtained from that finite window.
\item $R$ is the $\RegSeqRatUp$ readback row tying $D$ and $W$ back to the regular source $X$.
\item $E$ is the $\RealUp$ seal row exposed only after the budget, direction, window, dyadic positive-bound, and regular readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, apartness budget, comparison direction, modulus, window, positive dyadic bound, regular readback, Real seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from a comparison or apartness request through $X,A,O,M,W,D,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyApartnessOrderUp$, $\RegularCauchyApartnessBudgetUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyApartnessOrderUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite comparison packet. It has no coordinate for trichotomy, quotient real equality, host real inequality, a selected representative, total order decision, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy apartness-order NameCert obligations]
\label{thm:regular-cauchy-apartness-order-namecert-obligations}
For every accepted $\RegularCauchyApartnessOrderUp$ carrier $Q=(X,A,O,M,W,D,R,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyApartnessOrderUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the regular source, apartness budget, comparison direction, modulus, finite window, positive dyadic bound, regular readback, Real seal, transport, replay, provenance, and local naming rows;
\item classifier stability, requiring transported packets to preserve the same direction tag $O$, budget row $A$, window $W$, positive-bound row $D$, readback $R$, and seal $E$ componentwise through $H$ and $C$;
\item positive-boundary exactness, requiring every exported strict comparison or apartness read to pass through the displayed $\RegularCauchyApartnessBudgetUp$ row before reading the $\StreamNameUp$ window and $\DyadicRatCoreUp$ positive bound;
\item Real-seal non-escape, requiring the $\RealUp$ seal $E$ to remain downstream of $A,O,M,W,D$, and $R$ and never to serve as quotient equality, trichotomy, selected representative, host inequality, or completeness data;
\item ledger exclusions, requiring $P$ and $N$ to name exactly the displayed packet and to export no total order decision, no comparison by host real values, no quotient representative, and no ambient completion theorem.
\end{enumerate}
No regular Cauchy apartness-order obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyApartnessOrderUp.RegularCauchyApartnessOrderUpTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is the projection of \autoref{def:regular-cauchy-apartness-order-carrier}. The accepted packet exposes the source, budget, direction, modulus, window, positive-bound, readback, seal, and structural rows, and it has no additional comparison coordinate.

Classifier stability is componentwise. The transport row $H$ moves exactly the rows already displayed, and the replay row $C$ repeats the same comparison route after transport instead of recomputing it from host real values.

Positive-boundary exactness follows from the row order. A strict comparison or apartness read first exposes the budget row $A$, then the direction row $O$ and modulus row $M$, then the finite window $W$, and only then the dyadic positive-bound row $D$.

The Real-seal and ledger clauses are inventory consequences. Since $E$ is the only $\RealUp$ row and it is downstream of $A,O,M,W,D,R$, it cannot supply quotient equality, trichotomy, selected representatives, host inequality, or completeness. The provenance and local naming rows therefore exhaust the packet rather than opening any further order principle.
\end{proof}

\begin{theorem}[Regular Cauchy apartness-order positive boundary]
\label{thm:regular-cauchy-apartness-order-positive-boundary}
Every exported comparison or apartness read of an accepted $\RegularCauchyApartnessOrderUp$ carrier factors through the displayed route
$$
\RegularCauchyApartnessBudgetUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Concretely, a packet $Q=(X,A,O,M,W,D,R,E,H,C,P,N)$ exposes its comparison direction through $O$, consumes the positive budget $A$, reads the finite window $W$, obtains the positive dyadic boundary $D$, reattaches it to the regular source through $R$, and only then reaches the Real seal $E$. The sibling surfaces of \autoref{ch:concrete-instances-regular-cauchy-apartness-budget-namecert}, \autoref{ch:concrete-instances-bishoprealcomparison-namecert}, and \autoref{ch:concrete-instances-apartnessspace-namecert} are used only as displayed certificate rows, not as sources of trichotomy, quotient real equality, host inequality, selected representatives, total order decisions, or ambient completeness.
\end{theorem}
\begin{proof}
Start with an exported comparison or apartness read. By \autoref{thm:regular-cauchy-apartness-order-namecert-obligations}, it must be a read of the finite packet $Q$ and must preserve the displayed comparison direction row $O$.

The positive part of the read is forced through $A$. The budget row is the only public source of positive lower-bound data, so the consumer cannot reach a strict comparison or apartness assertion before the $\RegularCauchyApartnessBudgetUp$ route is displayed.

The finite observation route then passes through $W$ and $D$. The window row is a $\StreamNameUp$ inspection of the regular source, and the positive-bound row is a $\DyadicRatCoreUp$ read from that finite window.

Finally, $R$ reattaches the dyadic bound to the $\RegSeqRatUp$ source and $E$ provides the terminal $\RealUp$ seal. The comparison rows supplied by the BishopRealComparison and ApartnessSpace siblings remain boundary rows on this route; they do not add total comparison, quotient equality, host inequality, selected representatives, or completeness data.
\end{proof}

\begin{theorem}[Regular Cauchy apartness-order refusal boundary]
\label{thm:regular-cauchy-apartness-order-refusal-boundary}
An accepted $\RegularCauchyApartnessOrderUp$ packet exports only the finite surface
$$
X,A,O,M,W,D,R,E,H,C,P,N.
$$
Any consumer asking for trichotomy, quotient real equality, host real inequality, selected representatives, total order decisions, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking leaves the carrier surface.
\end{theorem}
\begin{proof}
Read the carrier inventory. The packet contains one regular source, one budget row, one comparison-direction row, one modulus row, one finite window, one positive dyadic bound, one regular readback, one Real seal, and the structural rows $H,C,P,N$.

Apply \autoref{thm:regular-cauchy-apartness-order-namecert-obligations}. The local NameCert obligations admit and transport exactly those fields, while positive-boundary exactness and Real-seal non-escape force all comparison reads through the same finite route.

The excluded objects are not packet coordinates. A consumer that asks for trichotomy, quotient equality, host inequality, a representative, a total order decision, choice, completeness, Lean verification, or bridge checking therefore asks for data outside $X,A,O,M,W,D,R,E,H,C,P,N$.
\end{proof}

\closureat{RegularCauchyApartnessOrderUp}{seedStr}

\begin{closurestatus}{\RegularCauchyApartnessOrderUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-apartness-order-carrier}, \autoref{thm:regular-cauchy-apartness-order-namecert-obligations}, \autoref{thm:regular-cauchy-apartness-order-positive-boundary}, and \autoref{thm:regular-cauchy-apartness-order-refusal-boundary} seed the constructive comparison boundary for regular Cauchy real names through finite apartness-budget, window, dyadic positive-bound, regular readback, and Real-seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close trichotomy, quotient real equality, host real inequality, selected representatives, total order decisions, countable choice, ambient $\RealUp$ completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, positive-boundary exactness, Real-seal non-escape, ledger exclusions, and refusal-boundary proofs for BEDC.Derived.RegularCauchyApartnessOrderUp.}
  \constructivestory{A $\RegularCauchyApartnessOrderUp$ packet is generated from a $\RegSeqRatUp$ source row, a $\RegularCauchyApartnessBudgetUp$ budget row, a displayed comparison-direction row, a modulus row, a $\StreamNameUp$ window, a $\DyadicRatCoreUp$ positive-bound readback, a $\RegSeqRatUp$ readback, a $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
