\chapter{A Concrete Naming Certificate for $\LocatedRealComparisonUp$}
\label{ch:concrete-instances-located-real-comparison-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\LocatedRealComparisonUp$ packet records the finite comparison surface for two located real presentations. It sits between \autoref{ch:concrete-instances-locatedreal-namecert}, \autoref{ch:concrete-instances-bishoprealcomparison-namecert}, \autoref{ch:concrete-instances-located-apartness-namecert}, \autoref{ch:concrete-instances-apartnessreal-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names the finite row surface by which a later order, density, or apartness consumer compares two displayed located-real endpoints without importing trichotomy, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, or a standard bridge.

\begin{definition}[Located real comparison carrier]
\label{def:located-real-comparison-carrier}
A $\LocatedRealComparisonUp$ carrier is a finite $\BHist$ packet
$$
K=(L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L_0$ and $L_1$ are the two $\LocatedRealUp$ endpoint rows. Each endpoint is read as a located real presentation before any comparison row is opened.
\item $W$ is the shared $\StreamNameUp$ window row. It records the common finite observation schedule used to inspect both endpoint presentations at the requested precision.
\item $R_0$ and $R_1$ are the two $\RegSeqRatUp$ readback rows attached to the windows of $L_0$ and $L_1$.
\item $D_0$ and $D_1$ are the two $\DyadicRatCoreUp$ endpoint and tolerance rows. They record the dyadic enclosures, slack budgets, and comparison tolerances used by the common window.
\item $B$ is the $\BishopRealComparisonUp$ row. It records the finite comparison request, its rational bracket data, and the displayed sign or overlap evidence available at the chosen window.
\item $A$ is the optional positive-gap handoff row. When the comparison exposes a positive separation, $A$ routes the same gap through the $\LocatedApartnessUp$ and $\ApartnessRealUp$ surfaces; when no positive gap is displayed, $A$ records the absent handoff and exports no apartness witness.
\item $H$ records componentwise $\hsame$ transport for both located-real endpoints, the shared window, both regular readbacks, both dyadic endpoint rows, the Bishop comparison row, the optional apartness handoff, continuation replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a comparison request through $L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedRealComparisonUp$, $\LocatedRealUp$, $\BishopRealComparisonUp$, $\LocatedApartnessUp$, $\ApartnessRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedRealComparisonUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite comparison packet for two displayed located real endpoints. The classifier compares accepted packets only through $L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N$, so it has no coordinate for trichotomy, total order of constructive reals, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, or a standard bridge.
\end{definition}
\leanchecked{BEDC.Derived.LocatedRealComparisonUp.LocatedRealComparisonUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located real comparison NameCert obligations]
\label{thm:located-real-comparison-namecert-obligations}
For every accepted $\LocatedRealComparisonUp$ carrier
$$
K=(L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N),
$$
the local $\NameCert_{\LocatedRealComparisonUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two $\LocatedRealUp$ endpoint rows, shared finite window, two regular readbacks, two dyadic endpoint and tolerance rows, Bishop comparison row, optional apartness handoff, transport, replay, provenance, and local naming rows;
\item shared-window discipline, requiring both endpoints to be inspected through the same $W$ before the comparison row $B$ is public;
\item readback exactness, requiring $R_0,R_1,D_0,D_1$ to supply the rational and dyadic data consumed by $B$ without exposing host endpoint values;
\item classifier transport, requiring $H$ to preserve componentwise sameness for the endpoint rows, window, readbacks, dyadic ledgers, comparison row, optional handoff row, and structural rows;
\item positive-gap handoff, requiring $A$ to export a $\LocatedApartnessUp$ or $\ApartnessRealUp$ witness only when the same displayed comparison data in $B$ and dyadic budget in $D_0,D_1$ exhibit a positive gap;
\item non-escape, refusing trichotomy, total order of constructive reals, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, and bridge checking as local NameCert data.
\end{enumerate}
No located-real comparison obligation is stored outside these six rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-real-comparison-carrier}. The projection exposes exactly the two located-real endpoints, the shared window, the two regular readbacks, the two dyadic ledgers, the Bishop comparison row, the optional apartness handoff, and the structural rows.

The shared-window obligation is read from $W$. Since both endpoint presentations are inspected through the same finite schedule before $B$ is public, a comparison consumer cannot compare one endpoint at a hidden precision or through an unrecorded stream request.

Readback exactness is the role of $R_0,R_1,D_0,D_1$. The regular rational rows supply finite endpoint observations, while the dyadic rows store the slack budgets and endpoint enclosures consumed by the Bishop comparison row.

Classifier transport is componentwise. The row $H$ preserves the endpoint, window, readback, dyadic, comparison, and optional handoff rows before $C,P,N$ replay, source, and name the same packet.

Finally, the positive-gap handoff is governed by $A$. A handoff to $\LocatedApartnessUp$ or $\ApartnessRealUp$ may occur only when the already displayed comparison and dyadic rows exhibit the gap; otherwise the row records absence. Thus trichotomy, total order, quotient real equality, selected representatives, countable choice, ambient completeness, Lean verification, and bridge checking never become local obligations.
\end{proof}

\begin{theorem}[Located real comparison shared-window stability]
\label{thm:located-real-comparison-window-stability}
Every accepted $\LocatedRealComparisonUp$ packet reads both endpoints through the same displayed $\StreamNameUp$ window before it exposes the comparison row. Consequently two accepted carriers matched componentwise by $L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N$ have the same finite comparison route and the same available positive-gap handoff status.
\end{theorem}
\begin{proof}
Inspect an accepted carrier $K=(L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N)$. The only window coordinate is $W$, and both endpoint readbacks cite this same finite observation schedule.

The comparison row $B$ is downstream of the endpoint rows, readbacks, and dyadic ledgers. Therefore changing the public comparison route would require changing at least one displayed coordinate among $L_0,L_1,W,R_0,R_1,D_0,D_1,B$.

The transport row $H$ moves these coordinates componentwise, while $C,P,N$ replay, source, and name the transported packet. The optional handoff $A$ is part of the same displayed route, so its present or absent status is stable under the same classifier match.
\end{proof}

\begin{theorem}[Located real comparison apartness handoff]
\label{thm:located-real-comparison-apartness-handoff}
If an accepted $\LocatedRealComparisonUp$ carrier exposes a positive-gap handoff row, then every downstream $\LocatedApartnessUp$ or $\ApartnessRealUp$ consumer of that gap factors through the displayed route
$$
(L_0,L_1)\longmapsto W\longmapsto(R_0,R_1)\longmapsto(D_0,D_1)\longmapsto B\longmapsto A\longmapsto H,C,P,N.
$$
If the handoff row is absent, the packet exports no apartness witness.
\end{theorem}
\begin{proof}
Start with a downstream consumer asking for apartness evidence from the comparison packet. The endpoint data available to that consumer are the displayed located-real rows $L_0$ and $L_1$, not host endpoint values.

The consumer must next read the common window $W$, the two regular readbacks $R_0,R_1$, and the dyadic endpoint budgets $D_0,D_1$. These rows supply the finite observations consumed by the Bishop comparison row $B$.

When $B$ and the dyadic budgets exhibit a positive gap, the handoff row $A$ routes that same evidence to the $\LocatedApartnessUp$ and $\ApartnessRealUp$ surfaces. When the row is absent, no consumer can project an apartness witness from the packet.

The structural rows $H,C,P,N$ transport, replay, source, and name the same finite route. Hence the handoff exports exactly the displayed positive-gap evidence and no trichotomy, total order, quotient real equality, selected representative, countable-choice selector, ambient completeness witness, or bridge data.
\end{proof}

\begin{theorem}[Located real comparison Real seal factorization]
\label{thm:located-real-comparison-real-seal-factorization}
Every accepted $\LocatedRealComparisonUp$ carrier
$$
K=(L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N)
$$
first reads the two $\LocatedRealUp$ endpoint rows $L_0,L_1$ and then factors their terminal $\RealUp$ seals through the shared finite readback route
$$
(L_0,L_1)\longmapsto W\longmapsto(R_0,R_1)\longmapsto(D_0,D_1)
$$
before exposing either the $\BishopRealComparisonUp$ row $B$ or the optional positive-gap handoff row $A$. Thus any downstream order, density, or apartness consumer of $B$ or $A$ reaches the two real seals only through the displayed $\StreamNameUp$ window, the two $\RegSeqRatUp$ readbacks, and the two $\DyadicRatCoreUp$ ledgers.
\end{theorem}
\begin{proof}
Project the carrier definition. The only endpoint coordinates are $L_0$ and $L_1$, and the comparison packet contains no separate host endpoint row or quotient-real representative from which $B$ or $A$ could be opened directly.

Apply \autoref{thm:located-real-comparison-window-stability}. The shared $W$ coordinate is the common $\StreamNameUp$ window for both endpoints, and the comparison route is stable only through the displayed coordinates $L_0,L_1,W,R_0,R_1,D_0,D_1,B,A,H,C,P,N$.

The two regular readbacks $R_0,R_1$ and the two dyadic ledgers $D_0,D_1$ are the finite rows that connect the endpoint presentations to the comparison row. Hence the terminal $\RealUp$ seals of the located endpoints are visible to $B$ only after this common readback route has been traversed.

Apply \autoref{thm:located-real-comparison-apartness-handoff} for the positive-gap branch. If $A$ is present, it exports only the same displayed gap already routed through $W,R_0,R_1,D_0,D_1$ and $B$; if $A$ is absent, it exports no apartness witness.

Consequently the factorization refuses host endpoint equality, quotient real equality, trichotomy, countable choice, ambient $\RealUp$ completeness, and bridge data. The public comparison and handoff surfaces are exactly the finite certified route named by the carrier.
\end{proof}

\closureat{LocatedRealComparisonUp}{seedStr}

\begin{closurestatus}{\LocatedRealComparisonUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-real-comparison-carrier}, \autoref{thm:located-real-comparison-namecert-obligations}, \autoref{thm:located-real-comparison-window-stability}, \autoref{thm:located-real-comparison-apartness-handoff}, and \autoref{thm:located-real-comparison-real-seal-factorization} seed the finite comparison route over two $\LocatedRealUp$ endpoints, a shared $\StreamNameUp$ window, two $\RegSeqRatUp$ readbacks, two $\DyadicRatCoreUp$ endpoint rows, a $\BishopRealComparisonUp$ row, and an optional $\LocatedApartnessUp$ or $\ApartnessRealUp$ positive-gap handoff.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.LocatedRealComparisonUp.LocatedRealComparisonUpTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close trichotomy, total order of constructive reals, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, shared-window discipline, readback exactness, classifier transport, positive-gap handoff, non-escape, and downstream apartness routing for BEDC.Derived.LocatedRealComparisonUp.}
  \constructivestory{A $\LocatedRealComparisonUp$ packet is generated from two displayed $\LocatedRealUp$ endpoint rows, one shared $\StreamNameUp$ window, two $\RegSeqRatUp$ readbacks, two $\DyadicRatCoreUp$ endpoint and tolerance ledgers, a $\BishopRealComparisonUp$ row, an optional positive-gap handoff through $\LocatedApartnessUp$ or $\ApartnessRealUp$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
