\chapter{A Concrete Naming Certificate for $\SequenceFilterBridgeUp$}
\label{ch:concrete-instances-sequence-filter-bridge-namecert}
\origin{human}

Following Bishop--Bridges regular-sequence completions and Kelley-style filterbase completions, the $\SequenceFilterBridgeUp$ packet records the finite bridge by which displayed regular sequence completion data and displayed Cauchy-filter completion data read the same completion surface. It sits between the sequence carrier of \autoref{ch:concrete-instances-cauchysequencespace-namecert}, the finite filterbase surface of \autoref{ch:concrete-instances-filterbase-namecert}, the filter completion handoff of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}, the sequential completeness boundary of \autoref{ch:concrete-instances-sequentiallycompletemetric-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a human-origin L10 Real and Completion bridge, not a quotient filter construction, selected limit, countable-choice selector, host equality comparison, or ambient completeness assumption.

\begin{definition}[Sequence-filter bridge carrier]\label{def:sequence-filter-bridge-carrier}
A $\SequenceFilterBridgeUp$ carrier is a finite $\BHist$ packet
$$
B=(S,F,Q,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the accepted $\CauchySequenceSpaceUp$ row, including the displayed sequence entries, Cauchy-modulus rows, tail-comparison rows, and provenance boundary.
\item $F$ is the accepted $\FilterBaseUp$ row generated from the same finite tail windows, with base packets indexed only by displayed precision requests and eventual-tail witnesses.
\item $Q$ is the $\CauchyFilterCompletionUp$ completion handoff read from $F$ after the filterbase directedness and Cauchy rows have been displayed.
\item $T$ is the $\StreamNameUp$ finite-window schedule common to the sequence side and the filterbase side.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the sequence windows and reused by the filterbase completion handoff.
\item $E$ is the $\RealUp$ seal row reached only after $S,F,Q,T,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the sequence row, filterbase row, completion handoff, stream schedule, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from sequence-completion reads to filter-completion reads and back along the same finite window schedule.
\item $P$ is the $\Pkg$ provenance over $\SequenceFilterBridgeUp$, $\CauchySequenceSpaceUp$, $\FilterBaseUp$, $\CauchyFilterCompletionUp$, $\SequentiallyCompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SequenceFilterBridgeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,F,Q,T,R,E,H,C,P,N$. It has no coordinate for quotient filters, selected limits, countable-choice selectors, host equality, or ambient completeness of the target metric or $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.SequenceFilterBridgeUp.SequenceFilterBridgeUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Sequence-filter bridge NameCert obligations]\label{thm:sequence-filter-bridge-namecert-obligations}
For every accepted $\SequenceFilterBridgeUp$ carrier $B=(S,F,Q,T,R,E,H,C,P,N)$, the local $\NameCert_{\SequenceFilterBridgeUp}$ surface consists exactly of:
\begin{enumerate}
\item carrier admission for the displayed ten-row packet;
\item sequence exposure through $S$, including displayed entries, Cauchy-modulus rows, tail-comparison rows, and source provenance;
\item filterbase exposure through $F$, with base packets generated from the same finite tail windows and precision requests;
\item completion handoff through $Q$, requiring the $\CauchyFilterCompletionUp$ read to cite the displayed filterbase rows of $F$;
\item shared-window readback through $T$ and $R$, requiring both directions of the bridge to use the same $\StreamNameUp$ schedule and $\RegSeqRatUp$ readback rows;
\item Real and sequential-completeness compatibility through $E$ and the $\SequentiallyCompleteMetricUp$ boundary, after the sequence, filterbase, completion, and readback rows have been displayed;
\item componentwise transport, continuation replay, package provenance, and local naming through $H,C,P,N$.
\end{enumerate}
No NameCert obligation may be discharged by a quotient filter, selected limit, countable choice, host equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:sequence-filter-bridge-carrier}. The rows $S,F,Q,T,R,E,H,C,P,N$ are the only coordinates available to the local classifier.

The sequence side is the row $S$. It exposes the finite Cauchy sequence data through \autoref{ch:concrete-instances-cauchysequencespace-namecert}, while $T$ and $R$ make the inspected windows and regular rational readback visible before any completion-facing handoff is read.

The filter side is generated from the same windows. The row $F$ records the $\FilterBaseUp$ packets built from displayed tails, and $Q$ reads the $\CauchyFilterCompletionUp$ handoff only after those packets have been exposed.

The compatibility rows close the obligation surface. The row $E$ seals the Real-facing read after the sequence, filterbase, completion, window, and readback rows have been displayed, while $H,C,P,N$ transport, replay, source, and name the same finite packet. Since the excluded principles have no coordinate in the carrier, the seven listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Sequence-to-filter route]\label{thm:sequence-filter-bridge-sequence-to-filter-route}
Every accepted sequence-completion read of a $\SequenceFilterBridgeUp$ carrier factors through the finite route
$$
\CauchySequenceSpaceUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \FilterBaseUp \longmapsto \CauchyFilterCompletionUp .
$$
In the notation of \autoref{def:sequence-filter-bridge-carrier}, the consumer reads $S$, then the shared schedule $T$ and readback $R$, then the filterbase row $F$, and only then the completion handoff $Q$ with its structural rows.
\end{theorem}
\begin{proof}
Start with a sequence-completion read of the bridge packet. By \autoref{def:sequence-filter-bridge-carrier}, the only sequence source coordinate is $S$, and every completion-facing observation from that coordinate is routed through the finite schedule $T$ and readback $R$.

The route then forms the filterbase row. The base packets in $F$ are indexed by the same displayed tail windows and precision requests, so no independent filter selector or quotient-filter equality is introduced.

Finally the completion handoff $Q$ reads \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}. The structural rows $H,C,P,N$ record that this is the same finite packet seen from the sequence side, so every accepted sequence-completion read reaches the filter completion surface through the displayed route.
\end{proof}

\begin{theorem}[Filter-to-sequence route]\label{thm:sequence-filter-bridge-filter-to-sequence-route}
Every accepted Cauchy-filter completion read of a $\SequenceFilterBridgeUp$ carrier factors back through the displayed sequence route
$$
\FilterBaseUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \CauchySequenceSpaceUp \longmapsto \SequentiallyCompleteMetricUp .
$$
The filter-facing consumer reads $F$, then the shared window schedule $T$ and readback $R$, then the sequence row $S$, and then the sequential-completeness boundary named in $P$.
\end{theorem}
\begin{proof}
Begin with a filter-completion read. The row $F$ supplies only the displayed finite filterbase packets, and $Q$ records the completion handoff attached to those packets.

The bridge exposes the same finite observations through $T$ and $R$. These rows determine which sequence windows and regular rational readbacks are visible, so the filter-facing route cannot choose an unrelated sequence representative.

The row $S$ then supplies the $\CauchySequenceSpaceUp$ packet, and $P$ records the $\SequentiallyCompleteMetricUp$ boundary used by the completion consumer. The replay row $C$ makes the reverse traversal explicit, while $H$ keeps the sequence, filterbase, completion, and readback rows componentwise transported together.
\end{proof}

\begin{theorem}[Sequence-filter bridge nonescape]\label{thm:sequence-filter-bridge-completion-nonescape}
Every $\RealUp$, $\RegSeqRatUp$, $\CauchyFilterCompletionUp$, or $\SequentiallyCompleteMetricUp$ consumer of an accepted $\SequenceFilterBridgeUp$ carrier $B=(S,F,Q,T,R,E,H,C,P,N)$ reads only the displayed sequence row, filterbase row, completion handoff, stream schedule, regular readback, Real seal, componentwise transport, continuation replay, provenance, and local NameCert row. The bridge exports no quotient filter, selected limit, countable-choice selector, host equality proof, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Project the downstream rows from \autoref{def:sequence-filter-bridge-carrier}. The only rows exposed to Real, regular-rational, filter-completion, or sequential-completeness consumers are $S,F,Q,T,R,E,H,C,P,N$.

The sequence and filter presentations share their finite observations. The rows $T$ and $R$ attach the inspected windows and regular readbacks to both $S$ and $F$, so neither side can escape to an unlisted representative, a quotient filter, or a selected limit.

The completion and Real-facing rows are downstream from the same finite route. The row $Q$ is read only after $F$, and the row $E$ is read only after $S,F,Q,T,R$ have been displayed.

The structural rows do not add hidden analytic data. They only transport, replay, source, and name the displayed rows. Therefore countable choice, host equality, and ambient completeness have no carrier row, continuation edge, or provenance slot from which to enter the bridge.
\end{proof}

\falsifiablePrediction{Every $\SequenceFilterBridgeUp$ completion read factors through a displayed CauchySequenceSpace source row, shared StreamName schedule, RegSeqRat readback, FilterBase row, CauchyFilterCompletion handoff, Real seal, transport, replay, provenance, and local naming.}

\independenceWitness{cauchysequencespace, filterbase, cauchyfiltercompletion, sequentiallycompletemetric, streamname, regseqrat, real: $\SequenceFilterBridgeUp$ is not bijective to any listed sibling because it carries the two directed bridge routes between displayed sequence completion data and displayed Cauchy-filter completion data in one finite packet.}

\closureat{SequenceFilterBridgeUp}{seedStr}

\begin{closurestatus}{\SequenceFilterBridgeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sequence-filter-bridge-carrier}, \autoref{thm:sequence-filter-bridge-namecert-obligations}, \autoref{thm:sequence-filter-bridge-sequence-to-filter-route}, \autoref{thm:sequence-filter-bridge-filter-to-sequence-route}, and \autoref{thm:sequence-filter-bridge-completion-nonescape} seed the finite bridge between regular sequence completion data and Cauchy-filter completion data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected limits, countable choice, host equality, ambient metric completeness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, sequence exposure, filterbase exposure, completion handoff, shared-window readback, Real and sequential-completeness compatibility, transport and replay stability, and nonescape for BEDC.Derived.SequenceFilterBridgeUp.}
  \constructivestory{A $\SequenceFilterBridgeUp$ packet is generated from a CauchySequenceSpace row, a FilterBase row on the same finite tail windows, a CauchyFilterCompletion handoff, a StreamName schedule, a RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
