\chapter{A Concrete Naming Certificate for $\CompleteSeparableMetricUp$}
\label{ch:concrete-instances-complete-separable-metric-namecert}
\origin{human}

Following Bishop and Bridges and Bourbaki, the $\CompleteSeparableMetricUp$ packet records the traditional complete separable metric surface as one finite L10 NameCert route. It joins the separable metric data of \autoref{ch:concrete-instances-separablemetric-namecert}, the completion route of \autoref{ch:concrete-instances-separable-completion-namecert}, the complete-metric boundary of \autoref{ch:concrete-instances-completemetric-namecert}, and the metric-completion interface of \autoref{ch:concrete-instances-metriccompletion-namecert}. Its observable route is read through the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the rational readback discipline of \autoref{ch:concrete-instances-regseqrat-namecert}, the real boundary of \autoref{ch:concrete-instances-real-namecert}, and the downstream complete-separable consumer surface of \autoref{ch:concrete-instances-polishspace-namecert}.

\begin{definition}[Complete separable metric carrier]\label{def:complete-separable-metric-carrier}
A $\CompleteSeparableMetricUp$ carrier is a finite $\BHist$ packet
$$
Q=(M,K,D,W,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the metric source row. It records the metric carrier, distance classifier, and the $\SeparableMetricUp$ countable-name surface over the same point histories.
\item $K$ is the complete-metric seal. It records the displayed $\CompleteMetricUp$ limit-witness handoff or the $\MetricCompletionUp$ admission route that supplies completion-facing convergence data.
\item $D$ is the separable dense schedule. It stores the countable dense enumeration, the request indices, and the finite visibility evidence needed to use density.
\item $W$ is the finite $\StreamNameUp$ window row. It is the only route through which dense indices, Cauchy observations, and completion-facing name segments are inspected.
\item $T$ is the $\DyadicRatCoreUp$ and $\RealUp$ tolerance ledger. It carries dyadic scales, Real distance boundaries, comparison budgets, and the finite tolerance rows attached to $W$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the dense schedule and tolerance ledger before the complete-metric seal is read.
\item $E$ is the $\RealUp$ boundary row. It records terminal distance or limit-boundary readings and has no coordinate for ambient completeness of $\RealUp$.
\item $H$ records componentwise $\hsame$ transport for the metric source, complete-metric seal, dense schedule, finite windows, tolerance ledger, regular readback, Real boundary, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from metric admission through dense-window reads, tolerance checks, regular readback, and complete-metric seal inspection.
\item $P$ is the $\Pkg$ provenance over $\CompleteSeparableMetricUp$, $\SeparableMetricUp$, $\SeparableCompletionUp$, $\CompleteMetricUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompleteSeparableMetricUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite complete-separable metric packet. It does not store quotient completion equality, selected dense points, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.CompleteSeparableMetricUp.CompleteSeparableMetricTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Complete separable metric NameCert obligations]\label{thm:complete-separable-metric-namecert-obligations}
For every accepted $\CompleteSeparableMetricUp$ carrier $Q=(M,K,D,W,T,R,E,H,C,P,N)$, the local $\NameCert_{\CompleteSeparableMetricUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the displayed metric source, complete-metric seal, dense schedule, finite windows, tolerance ledger, regular readback, Real boundary, transport, replay, provenance, and local naming rows;
\item complete-metric handoff, requiring the convergence or completion-facing seal $K$ to be read from the same metric source that supplies $M$ and never from a second host completion object;
\item countable-density visibility, requiring every density request to pass through the displayed schedule $D$ and a finite $\StreamNameUp$ window $W$;
\item tolerance discipline, requiring dyadic and Real comparison budgets in $T$ before any completion-facing approximation is exposed;
\item regular readback, requiring the $\RegSeqRatUp$ row $R$ to mediate finite rational observations before the complete-metric seal is inspected;
\item Real-seal nonescape, requiring the boundary row $E$ to remain a terminal distance or limit reading rather than a proof of ambient $\RealUp$ completeness;
\item ledger nonescape, excluding quotient completion equality, selected dense points, countable-choice selectors, open-cover compactness, and any hidden completion equality from the packet.
\end{enumerate}
No complete-separable metric obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:complete-separable-metric-carrier}. The projection exposes exactly the metric source $M$, complete-metric seal $K$, dense schedule $D$, finite window $W$, tolerance ledger $T$, regular readback $R$, Real boundary $E$, and structural rows $H,C,P,N$.

Carrier admission and complete-metric handoff are tied to the same metric source. The rows $M$ and $K$ are transported together by $H$, and the replay row $C$ permits the completion-facing seal only after the source metric route has been displayed.

Density visibility is finite. A consumer reaches a dense candidate through the indexed schedule $D$ and a displayed $\StreamNameUp$ window $W$, then reads the tolerance ledger $T$ and regular rational row $R$ before consulting $K$ or $E$.

The nonescape clauses follow from the carrier shape. None of the rows stores quotient completion equality, selected dense points, a countable-choice selector, open-cover compactness, hidden completion equality, or ambient $\RealUp$ completeness, so the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Complete separable metric density-completion handoff]\label{thm:complete-separable-metric-density-completion-handoff}
Every $\PolishSpaceUp$ or completion-facing consumer of an accepted $\CompleteSeparableMetricUp$ carrier $Q=(M,K,D,W,T,R,E,H,C,P,N)$ reads the finite route
$$
M,D \longmapsto W \longmapsto T \longmapsto R \longmapsto K \longmapsto E \longmapsto H,C,P,N
$$
before it reads the public packet. Thus density, finite observation, tolerance, regular readback, and complete-metric seal data remain visible to the consumer, while quotient completion equality, selected dense points, countable choice, open-cover compactness, and ambient $\RealUp$ completeness remain outside the packet.
\end{theorem}
\begin{proof}
Begin with a $\PolishSpaceUp$ or completion-facing read of $Q$. Carrier admission gives the consumer the metric source and dense schedule only as the displayed pair $M,D$.

Replay the observation route. The request opens the finite $\StreamNameUp$ window $W$, reads the dyadic or Real tolerance ledger $T$, and obtains the $\RegSeqRatUp$ readback $R$ before the complete-metric seal $K$ is available.

The Real boundary and public packaging are downstream. The row $E$ records only terminal distance or limit-boundary data, while $H,C,P,N$ transport, replay, source, and name the same finite route.

Therefore every downstream consumer reads the dense schedule, finite windows, tolerance ledger, regular readback, and complete-metric seal before the public packet. The excluded quotient, selected-point, choice, compactness, hidden-completion, and ambient-Real-completeness data have no coordinate in the carrier.
\end{proof}

\closureat{CompleteSeparableMetricUp}{seedStr}
\begin{closurestatus}{\CompleteSeparableMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-separable-metric-carrier}, \autoref{thm:complete-separable-metric-namecert-obligations}, and \autoref{thm:complete-separable-metric-density-completion-handoff} seed the finite complete-separable route through metric source data, complete-metric seals, dense schedules, finite windows, tolerance ledgers, regular readbacks, and Real boundary rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected dense points, countable choice, open-cover compactness, hidden completion equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, complete-metric handoff, countable-density visibility, tolerance discipline, regular readback, Real-seal nonescape, ledger nonescape, and density-completion handoff for BEDC.Derived.CompleteSeparableMetricUp.}
  \constructivestory{A $\CompleteSeparableMetricUp$ packet is generated from a metric and separable source row, a complete-metric or metric-completion seal, a countable dense schedule, finite StreamName windows, DyadicRatCore or RealUp tolerance data, a RegSeqRat readback, a terminal RealUp boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
