\chapter{A Concrete Naming Certificate for $\RegularCauchyTailModulusUp$}
\label{ch:concrete-instances-regular-cauchy-tail-modulus-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyTailModulusUp$ packet records the finite precision-to-tail threshold service used by regular Cauchy real names before any completed limit, quotient stream equality, or choice-selected modulus is available. It reads the finite window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational source route of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the displayed tail-diameter witness of \autoref{ch:concrete-instances-cauchy-tail-diameter-namecert}, and the shared-window budget of \autoref{ch:concrete-instances-uniform-cauchy-modulus-namecert}. The packet names the one-source threshold row that later $\RegSeqRatUp$, $\RealUp$, $\CauchyTailDiameterUp$, and $\UniformCauchyModulusUp$ consumers may cite when a requested precision must be turned into a visible finite tail service.

\begin{definition}[Regular Cauchy tail modulus carrier]
\label{def:regular-cauchy-tail-modulus-carrier}
A $\RegularCauchyTailModulusUp$ carrier is a finite $\BHist$ packet
$$
K=(S,Q,T,W,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\RegSeqRatUp$ source row whose regular Cauchy tail service is being queried.
\item $Q$ is the precision-request row, recording the requested dyadic tolerance as a visible consumer input.
\item $T$ is the displayed tail-threshold row returned for the request $Q$ on the source $S$.
\item $W$ is the finite $\StreamNameUp$ window service showing which source observations are visible once the threshold $T$ has been read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row against which the displayed request and tail observations are compared.
\item $H$ records componentwise $\hsame$ transport for the source, request, threshold, window service, dyadic tolerance, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the source and precision request through the threshold, the finite window service, and the dyadic tolerance row.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyTailModulusUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CauchyTailDiameterUp$, $\UniformCauchyModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTailModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,Q,T,W,D,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy tail modulus NameCert obligations]
\label{thm:regular-cauchy-tail-modulus-namecert-obligations}
For every accepted $\RegularCauchyTailModulusUp$ carrier $K=(S,Q,T,W,D,H,C,P,N)$, the local $\NameCert_{\RegularCauchyTailModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the regular source, precision request, displayed threshold, finite window service, dyadic tolerance, transport, replay, provenance, and local naming rows;
\item request exactness, requiring $Q$ to be the precision request consumed by the source row $S$ and by no detached schedule;
\item tail-threshold exactness, requiring $T$ to be the displayed tail threshold returned for the pair $(S,Q)$;
\item window handoff, requiring $W$ to expose only finite $\StreamNameUp$ observations available after the threshold $T$ is read;
\item dyadic tolerance compatibility, requiring the request row $Q$ and all tail-window comparisons exported through $W$ to be checked against the same $\DyadicRatCoreUp$ row $D$;
\item transport and replay stability, requiring $H$ and $C$ to preserve the same source-request-threshold-window-tolerance route;
\item provenance and local naming, requiring $P$ and $N$ to package exactly the displayed rows $S,Q,T,W,D,H,C$;
\item refusal of quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, and bridge checking as local NameCert obligations.
\end{enumerate}
No regular Cauchy tail-modulus obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyTailModulusUp.RegularCauchyTailModulusTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy tail modulus window handoff]
\label{thm:regular-cauchy-tail-modulus-window-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer that uses a tail threshold from an accepted $\RegularCauchyTailModulusUp$ carrier must read the rows in the order
$$
S,Q,T,W,D,H,C,P,N .
$$
Thus the consumer sees the regular source, the requested precision, the displayed threshold, the finite window service, the dyadic tolerance row, transport, replay, provenance, and local naming before using the threshold. The route exports no quotient stream equality, selected limit, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}

\begin{definition}[Regular Cauchy tail modulus diameter-control carrier]
\label{def:regular-cauchy-tail-modulus-diameter-control-carrier}
A diameter-control $\RegularCauchyTailModulusUp$ carrier is a finite $\BHist$ packet
$$
K^{\diamondsuit}=(S,Q,T,W,D,B,U,H,C,P,N)
$$
whose first five rows are the regular source $S$, precision request $Q$, displayed threshold $T$, finite window $W$, and $\DyadicRatCoreUp$ tolerance $D$ of \autoref{def:regular-cauchy-tail-modulus-carrier}. The row $B$ is a $\CauchyTailDiameterUp$ certificate row over the same $S,Q,T,W,D$ route, and the row $U$ is a $\UniformCauchyModulusUp$ consumer row over the same source, request, threshold, window, tolerance, and diameter-control row. The remaining rows $H,C,P,N$ record componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\RegularCauchyTailModulusUp}$ packaging for exactly these displayed rows.

The classifier compares accepted packets only through $S,Q,T,W,D,B,U,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy tail modulus diameter control]
\label{thm:regular-cauchy-tail-modulus-diameter-control}
If a diameter-control $\RegularCauchyTailModulusUp$ carrier
$$
K^{\diamondsuit}=(S,Q,T,W,D,B,U,H,C,P,N)
$$
is accepted, then every two displayed tail indices beyond the threshold row $T$ read their diameter bound through the $\CauchyTailDiameterUp$ row $B$ after the shared route $S,Q,T,W,D$ and before the structural rows $H,C,P,N$. Thus the threshold is a concrete finite diameter-control service: the same source, precision request, threshold, finite window, and dyadic tolerance that admit the tail handoff also admit the displayed tail-diameter bound.

The conclusion uses no quotient stream equality, selected limit, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge data.
\end{theorem}

\begin{proof}
Read the accepted packet by projection. The first five projections recover the route $S,Q,T,W,D$, and \autoref{thm:regular-cauchy-tail-modulus-window-handoff} forces any consumer of the threshold to pass through that route before the structural rows are available.

Apply the finite-window reading of \autoref{ch:concrete-instances-cauchy-tail-diameter-namecert} to the displayed row $B$. Since $B$ is part of the same accepted packet and its carrier coordinates are exactly $S,Q,T,W,D$, every pair of visible tail indices beyond $T$ obtains its bound from the same finite window and the same $\DyadicRatCoreUp$ tolerance row.

The remaining rows $H,C,P,N$ only transport, replay, package, and name the displayed data. They add no equality of quotient streams, no selected limit, no choice principle, no trichotomy, no compactness principle, no ambient completeness claim, and no bridge datum.
\end{proof}

\begin{theorem}[Regular Cauchy tail modulus uniform window consumption]
\label{thm:regular-cauchy-tail-modulus-uniform-window-consumption}
Every $\UniformCauchyModulusUp$ consumer using the threshold $T$ of an accepted diameter-control $\RegularCauchyTailModulusUp$ carrier must first consume the same route
$$
S,Q,T,W,D,B
$$
before reading its local uniform-modulus row $U$ or the structural rows $H,C,P,N$. Consequently the uniform modulus is not a detached schedule: it is a finite-window consumer of the displayed source, request, threshold, window, dyadic tolerance, and $\CauchyTailDiameterUp$ diameter-control row.
\end{theorem}

\begin{proof}
Project the accepted packet to the threshold route and then to the diameter-control row. The preceding theorem supplies the finite tail-diameter service through $B$, so any consumer that claims to use the same threshold already has the route $S,Q,T,W,D,B$ in view.

Apply the shared-window budget described by \autoref{ch:concrete-instances-uniform-cauchy-modulus-namecert}. The $\UniformCauchyModulusUp$ row $U$ is admitted only as a consumer over the displayed route, so its scheduling data is read after the diameter-control row and cannot be separated from the finite window that witnesses the tail bound.

The structural rows preserve this dependency by transport, replay, provenance, and local naming. They do not introduce quotient stream equality, selected limits, choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge data.
\end{proof}

\closureat{RegularCauchyTailModulusUp}{seedStr}

\begin{closurestatus}{\RegularCauchyTailModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-tail-modulus-carrier}, \autoref{thm:regular-cauchy-tail-modulus-namecert-obligations}, \autoref{thm:regular-cauchy-tail-modulus-window-handoff}, \autoref{def:regular-cauchy-tail-modulus-diameter-control-carrier}, \autoref{thm:regular-cauchy-tail-modulus-diameter-control}, and \autoref{thm:regular-cauchy-tail-modulus-uniform-window-consumption} seed the finite precision-to-tail threshold packet over RegSeqRat source rows, dyadic precision requests, displayed thresholds, finite StreamName window services, DyadicRatCore tolerances, CauchyTailDiameter rows, UniformCauchyModulus rows, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, request exactness, tail-threshold exactness, window handoff, dyadic tolerance compatibility, transport, replay, provenance, and local naming for future BEDC.Derived.RegularCauchyTailModulusUp obligations.}
  \constructivestory{A $\RegularCauchyTailModulusUp$ packet is generated from a RegSeqRat source row, a precision request, a displayed tail threshold, a finite StreamName window service, a DyadicRatCore tolerance row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
