\chapter{A Concrete Naming Certificate for $\ClosedIntervalCauchyCompletionUp$}
\label{ch:concrete-instances-closed-interval-cauchy-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\ClosedIntervalCauchyCompletionUp$ packet records the finite closed-interval route by which endpoint bounds, interval nets, stream windows, regular rational readbacks, dyadic tolerance ledgers, and the Bishop regular Cauchy completion boundary are assembled before a Real-facing seal is consumed. It sits over the closed bounded interval net of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}, the finite observation surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Bishop regular Cauchy completion packet of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives Real and Completion consumers a finite closed-interval completion surface; it does not import Heine--Borel compactness, open-cover compactness, selected limits, quotient streams, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Closed interval Cauchy completion carrier]
\label{def:closed-interval-cauchy-completion-carrier}
A $\ClosedIntervalCauchyCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(A,B,I,S,R,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the lower closed endpoint row and $B$ is the upper closed endpoint row, both read through the same finite endpoint discipline as the source closed interval.
\item $I$ is the $\ClosedBoundedIntervalNetUp$ row, recording the finite interval net, mesh scale, endpoint containment route, and interval-local coverage data consumed by the completion request.
\item $S$ is the $\StreamNameUp$ finite-window row opened by the interval-net request before any regular rational readback is exposed.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed StreamName windows and endpoint-bounded interval route.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic radius, endpoint comparison budget, common denominator budget, and tail allowance used by the interval Cauchy read.
\item $Q$ is the $\BishopRegularCauchyCompletionUp$ handoff row, consuming $A,B,I,S,R,D$ before any Real-facing completion boundary is visible.
\item $E$ is the terminal $\RealUp$ seal row reached only after the endpoint rows, interval-net row, finite windows, regular readback, dyadic tolerance ledger, and Bishop completion handoff have been displayed.
\item $H$ records componentwise $\hsame$ transport for endpoints, interval-net data, StreamName windows, RegSeqRat readbacks, dyadic tolerance ledgers, Bishop completion handoff, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a closed-interval completion request through $A,B,I,S,R,D,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\ClosedIntervalCauchyCompletionUp$, $\ClosedBoundedIntervalNetUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BishopRegularCauchyCompletionUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ClosedIntervalCauchyCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,B,I,S,R,D,Q,E,H,C,P,N$. The carrier has no coordinate for open-cover compactness, selected limits, quotient streams, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.ClosedIntervalCauchyCompletionUp.ClosedIntervalCauchyCompletionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Closed interval Cauchy completion NameCert obligations]
\label{thm:closed-interval-cauchy-completion-namecert-obligations}
For every accepted $\ClosedIntervalCauchyCompletionUp$ carrier
$$
K=(A,B,I,S,R,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\ClosedIntervalCauchyCompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the lower endpoint, upper endpoint, ClosedBoundedIntervalNet row, StreamName finite windows, RegSeqRat readback, DyadicRatCore tolerance ledger, Bishop regular Cauchy completion handoff, Real seal, transport, replay, provenance, and local naming rows;
\item endpoint-bounded interval admission, requiring the interval-net row $I$ to be read from the displayed endpoint rows $A,B$ rather than from a host closed interval;
\item finite-window locality, requiring $S$ to expose exactly the stream observations opened by the interval-net request and the dyadic tolerance ledger $D$;
\item regular readback locality, requiring $R$ to be read only from the displayed StreamName windows and endpoint-bounded interval route;
\item completion handoff ordering, requiring $Q$ to consume $A,B,I,S,R,D$ before $E$ exposes the terminal $\RealUp$ seal;
\item componentwise classifier transport, displayed replay, provenance, and local naming for the same displayed rows through $H,C,P,N$;
\item ledger non-escape, requiring the packet to export no open-cover compactness, selected limit, quotient stream, countable-choice schedule, trichotomy branch, host real equality, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
No closed-interval Cauchy completion obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:closed-interval-cauchy-completion-carrier}. The visible packet consists exactly of the two endpoint rows $A,B$, the interval-net row $I$, finite windows $S$, regular readback $R$, dyadic tolerance ledger $D$, Bishop completion handoff $Q$, terminal seal $E$, and structural rows $H,C,P,N$.

Endpoint-bounded interval admission is upstream of every completion read. The row $I$ is the only interval-net coordinate, and it is attached to the displayed endpoints $A,B$, so a consumer cannot replace it by a host closed interval or by an unrecorded compactness theorem.

Finite-window and regular readback locality are the middle route. The StreamName row $S$ opens exactly the observations allowed by $I$ and $D$, and the RegSeqRat row $R$ reads only those displayed windows before any completion handoff is available.

The completion handoff then follows the displayed order. The row $Q$ consumes $A,B,I,S,R,D$, and the terminal Real seal $E$ is exposed only after that handoff has been displayed.

Finally, $H,C,P,N$ transport, replay, package, and name the same finite route. Since none of the excluded objects occurs in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Closed interval Cauchy completion route]
\label{thm:closed-interval-cauchy-completion-route}
Every Real or Completion consumer that reads an accepted $\ClosedIntervalCauchyCompletionUp$ carrier factors its request through the finite route
$$
A,B \longmapsto I \longmapsto S \longmapsto R \longmapsto D \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Consequently the consumer receives displayed closed endpoints, a ClosedBoundedIntervalNet row, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a Bishop regular Cauchy completion handoff, a terminal RealUp seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row. The route supplies no open-cover compactness, selected limit, quotient stream, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier $K=(A,B,I,S,R,D,Q,E,H,C,P,N)$. The endpoint rows $A,B$ and the interval-net row $I$ are the only closed-interval source coordinates available to a consumer.

The finite observation route is then forced by the packet. The StreamName row $S$ opens the window selected by the interval-net request, and the RegSeqRat row $R$ reads back that window inside the displayed endpoint bounds.

The tolerance and completion boundary are downstream. The DyadicRatCore row $D$ records the dyadic radius and comparison budget, the Bishop regular Cauchy completion row $Q$ consumes the endpoint, net, window, readback, and tolerance rows, and the Real seal $E$ is reached only after that handoff.

The remaining rows preserve the same route under componentwise $\hsame$ transport and displayed $\Cont$ replay, with $P$ and $N$ recording provenance and local naming. Since no excluded compactness, selection, quotient, choice, trichotomy, host-equality, or ambient-completeness coordinate is present, every public read is exhausted by the displayed route.
\end{proof}

\falsifiablePrediction{Every $\ClosedIntervalCauchyCompletionUp$ read factors through displayed closed endpoints, one ClosedBoundedIntervalNet row, finite StreamName windows, one RegSeqRat readback row, one DyadicRatCore tolerance ledger, one BishopRegularCauchyCompletion handoff, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{closedboundedintervalnet, streamname, regseqrat, dyadicratcore, bishop-regular-cauchy-completion, real: $\ClosedIntervalCauchyCompletionUp$ is not bijective to any listed sibling because it jointly carries endpoint-bounded interval-net data, finite observation windows, regular rational readback, dyadic tolerance accounting, the Bishop completion handoff, and the terminal Real seal as one closed-interval completion packet.}

\closureat{ClosedIntervalCauchyCompletionUp}{seedStr}

\begin{closurestatus}{\ClosedIntervalCauchyCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-interval-cauchy-completion-carrier}, \autoref{thm:closed-interval-cauchy-completion-namecert-obligations}, and \autoref{thm:closed-interval-cauchy-completion-route} seed the finite closed-interval Cauchy completion route from displayed endpoints and interval-net rows through StreamName windows, RegSeqRat readback, DyadicRatCore tolerance accounting, Bishop regular Cauchy completion handoff, Real seal, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected limits, quotient streams, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint-bounded interval admission, finite-window locality, regular readback locality, completion handoff ordering, classifier transport, replay, provenance, local naming, and route factorization for BEDC.Derived.ClosedIntervalCauchyCompletionUp.}
  \constructivestory{A $\ClosedIntervalCauchyCompletionUp$ packet is generated from displayed closed endpoint rows, one ClosedBoundedIntervalNet row, finite StreamName windows, one RegSeqRat readback row, one DyadicRatCore tolerance ledger, one BishopRegularCauchyCompletion handoff, one terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
