\chapter{A Concrete Naming Certificate for $\RealCompletionExactBoundaryUp$}
\label{ch:concrete-instances-real-completion-exact-boundary-namecert}
\origin{ai}

The $\RealCompletionExactBoundaryUp$ packet is the finite boundary surface for the Real completion route of \autoref{ch:visions-real-completeness}. It sits after the seal route of \autoref{ch:concrete-instances-cauchylimitseal-namecert}, the completion-seal classifier of \autoref{ch:concrete-instances-real-completion-seal-classifier-namecert}, the witness ledger of \autoref{ch:concrete-instances-cauchy-witness-ledger-namecert}, the synchronizer of \autoref{ch:concrete-instances-cauchy-seal-budget-synchronizer-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. Its role is to bind those existing rows into one exact finite NameCert packet, not to add quotient streams, selected host limits, countable choice, host real equality, or ambient completeness.

\falsifiablePrediction{If a Real completion boundary read bypasses either the displayed seal/classifier rows or the displayed witness/budget rows, the packet is refuted.}

\independenceWitness{cauchylimitseal, realcompletionsealclassifier, cauchywitnessledger, cauchysealbudgetsynchronizer, real: no listed sibling contains the exact joint seal, classifier, witness-ledger, synchronizer, StreamName, RegSeqRat, DyadicRatCore, and RealUp packet surface.}

\begin{definition}[Real completion exact-boundary carrier]
\label{def:real-completion-exact-boundary-carrier}
A $\RealCompletionExactBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\CauchyLimitSealUp$ seal row consumed by the completion route;
\item $K$ is the $\RealCompletionSealClassifierUp$ classifier row for the same displayed seal surface;
\item $J$ is the $\CauchyWitnessLedgerUp$ row naming the finite witness evidence for the route;
\item $S$ is the $\CauchySealBudgetSynchronizerUp$ row synchronizing the seal budget with the witness ledger;
\item $W$ is the $\StreamNameUp$ finite-window row read by the same route;
\item $R$ is the $\RegSeqRatUp$ regular-rational readback row attached to $W$;
\item $D$ is the $\DyadicRatCoreUp$ dyadic tolerance and endpoint row used by the readback;
\item $E$ is the terminal $\RealUp$ seal row reached only after $L,K,J,S,W,R,D$ have been displayed;
\item $H$ records componentwise $\hsame$ transports for all displayed rows;
\item $C$ records the displayed $\Cont$ replay from seal and witness admission to the terminal Real seal;
\item $P$ is the $\Pkg$ provenance over the sibling certificates, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RealCompletionExactBoundaryUp}$ row.
\end{enumerate}
The classifier compares carriers only through these rows. It has no coordinate for quotient stream equality, host real equality, a hidden selector, a second seal route, a detached witness ledger, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Real completion exact-boundary NameCert obligations]
\label{thm:real-completion-exact-boundary-namecert-obligations}
For every accepted $\RealCompletionExactBoundaryUp$ carrier
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\RealCompletionExactBoundaryUp}$ surface consists exactly of carrier exposure for $B$, completion-seal exposure through $L$, classifier exposure through $K$, witness-ledger exposure through $J$, synchronized budget exposure through $S$, finite-window exposure through $W$, regular-rational readback through $R$, dyadic tolerance readback through $D$, terminal $\RealUp$ seal exposure through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryNameCertObligations}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}. Its displayed packet lists the seal row, classifier row, witness ledger, budget synchronizer, finite window, regular-rational readback, dyadic ledger, terminal Real seal, and structural rows.

Read the sibling dependencies in order. The completion seal $L$ and classifier $K$ fix the seal-facing side, while the witness ledger $J$ and synchronizer $S$ fix the evidence and budget side. The rows $W,R,D,E$ are then the StreamName, RegSeqRat, DyadicRatCore, and RealUp projections of that same route.

The structural rows $H,C,P,N$ only transport, replay, record provenance for, and name the displayed packet. Since no other coordinate is present in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real completion exact-boundary non-escape]
\label{thm:real-completion-exact-boundary-nonescape}
Every accepted $\RealCompletionExactBoundaryUp$ consumer factors through the finite route
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
The consumer may inspect the completion seal, seal classifier, witness ledger, synchronized budget, StreamName window, RegSeqRat readback, DyadicRatCore tolerance ledger, RealUp seal, componentwise transports, continuations, provenance, and local NameCert row. It receives no quotient stream equality, host real equality, hidden selector, second seal route, detached witness ledger, or ambient completeness coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryNonescape}
\begin{proof}
Start from the accepted packet $B=(L,K,J,S,W,R,D,E,H,C,P,N)$. The seal/classifier side and the witness/budget side are both displayed before the StreamName, RegSeqRat, DyadicRatCore, and RealUp rows can be consumed as boundary projections.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The local certificate exports exactly the rows $L,K,J,S,W,R,D,E,H,C,P,N$ and treats $H,C,P,N$ as structural support for that same finite packet.

Finally inspect the excluded objects. Quotient stream equality, host real equality, hidden selectors, second seal routes, detached witness ledgers, and ambient completeness are absent from the carrier and classifier. A consumer that reads any of them has left the accepted exact-boundary packet.
\end{proof}

\begin{theorem}[Real completion StreamName--RegSeq route]
\label{thm:real-completion-exact-boundary-streamname-regseq-route}
Every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
routes the completion read through the finite chain $W,R,D,E,H,C,P,N$ after the seal, classifier, witness, and synchronizer rows $L,K,J,S$ have been displayed. In that route, $W$ supplies the $\StreamNameUp$ finite-window row, $R$ supplies the $\RegSeqRatUp$ readback row for the same window, $D$ supplies the $\DyadicRatCoreUp$ tolerance and endpoint row consumed by that readback, and $E$ supplies the terminal $\RealUp$ seal reached by the displayed completion packet.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryStreamNameRegSeq\_route}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}. The coordinates $W,R,D,E$ occur as named rows of the same accepted packet as $L,K,J,S,H,C,P,N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The local NameCert obligations expose the StreamName finite window, RegSeqRat readback, DyadicRatCore tolerance ledger, and RealUp seal as part of one certificate surface, with $H,C,P,N$ transporting, replaying, packaging, and naming that surface.

Use \autoref{thm:real-completion-exact-boundary-nonescape}. Any completion consumer that attempts to read $W,R,D$, or $E$ outside the displayed route would require an absent coordinate, so the completion read is forced through the finite packet $W,R,D,E,H,C,P,N$ under the already displayed rows $L,K,J,S$.
\end{proof}

\begin{theorem}[Real completion terminal seal non-escape]
\label{thm:real-completion-exact-boundary-real-seal-nonescape}
No terminal $\RealUp$ seal read accepted by a $\RealCompletionExactBoundaryUp$ packet can bypass the displayed route
$$
L,K,J,S,W,R,D,E,H,C,P,N
$$
by using quotient stream equality, host real equality, a hidden selector, a second seal route, a detached witness ledger, or ambient completeness. The only accepted terminal seal read is the row $E$ reached through the carrier, NameCert obligations, and non-escape surface of the same finite packet.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryRealSealNonescape}
\begin{proof}
Begin with the carrier. The row $E$ is displayed as the terminal $\RealUp$ seal only after the seal row $L$, classifier row $K$, witness ledger $J$, synchronizer row $S$, StreamName row $W$, RegSeqRat row $R$, and DyadicRatCore row $D$ are present.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The certificate exports no equality quotient on streams, no host real equality coordinate, no selector coordinate, no alternate seal route, no detached ledger, and no ambient completeness witness.

Finally apply \autoref{thm:real-completion-exact-boundary-nonescape}. Since every accepted consumer factors through $L,K,J,S,W,R,D,E,H,C,P,N$, any terminal seal read that uses one of the excluded routes is outside the packet rather than an accepted Real seal read.
\end{proof}

\begin{theorem}[Real completion exact-boundary four-face exactness]
\label{thm:real-completion-exact-boundary-four-face-exactness}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the accepted completion boundary exposes exactly the four Phase Real and Completion faces $\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and $\RealUp(E)$ after the seal, classifier, witness-ledger, and budget rows $L,K,J,S$. Every completion-facing consumer and every terminal Real-seal consumer factors through the structural rows $H,C,P,N$ of the same packet. No quotient stream row, host real equality row, selected limit row, countable-choice row, ambient-completeness row, metric-completeness row, or bridge row is exported by the boundary.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}. Its displayed rows place $L,K,J,S$ first, followed by the four boundary faces $W,R,D,E$ and the structural rows $H,C,P,N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The local certificate identifies the complete row inventory of the accepted packet, so the only Phase Real and Completion face rows available after $L,K,J,S$ are $W$, $R$, $D$, and $E$.

Apply \autoref{thm:real-completion-exact-boundary-streamname-regseq-route}. The ordered route reads $W$ as the $\StreamNameUp$ finite-window face, $R$ as the $\RegSeqRatUp$ readback face, $D$ as the $\DyadicRatCoreUp$ tolerance face, and $E$ as the terminal $\RealUp$ seal face.

Finally use \autoref{thm:real-completion-exact-boundary-real-seal-nonescape} together with \autoref{thm:real-completion-exact-boundary-nonescape}. The first theorem blocks terminal Real-seal escape, and the second blocks completion-boundary escape, so any consumer of the accepted boundary must pass through $H,C,P,N$ and receives none of the excluded quotient, host-equality, selected-limit, choice, completeness, or bridge coordinates.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryFourFaceExactness}

\begin{theorem}[Real completion exact-boundary finite-tail-filter handoff]
\label{thm:real-completion-exact-boundary-finite-tail-filter-handoff}
Every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
whose completion boundary is read through a finite cofinal-tail filter must consume the displayed $\FiniteTailFilterUp$ packet of \autoref{ch:concrete-instances-finite-tail-filter-namecert} before any completion-facing or terminal Real-seal consumer reads the boundary. Equivalently, the four faces $\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and $\RealUp(E)$ factor through that finite-tail-filter packet, with no quotient stream row, host real equality row, selected limit row, countable-choice row, ambient-completeness row, metric-completeness row, or bridge row inserted between the cofinal-tail handoff and the accepted boundary.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryFiniteTailFilterHandoff}
\begin{proof}
Start with \autoref{thm:real-completion-exact-boundary-four-face-exactness}. It identifies the only completion and Real faces exported by the accepted boundary as $\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and $\RealUp(E)$, all after the rows $L,K,J,S$ and before the structural rows $H,C,P,N$ are consumed.

Apply \autoref{thm:real-completion-exact-boundary-streamname-regseq-route}. The displayed route orders the same four faces as a StreamName window, regular-rational readback, dyadic tolerance ledger, and terminal Real seal, so a completion-boundary read through a finite cofinal-tail filter has no separate route on which to read those faces.

Now use \autoref{thm:finite-tail-filter-sibling-tail-handoff}. The finite-tail-filter packet is exactly the sibling handoff surface for StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, and the Real seal. Hence the four displayed faces of the exact boundary must pass through that packet whenever the boundary is presented through a finite cofinal-tail filter.

Finally apply \autoref{thm:finite-tail-filter-real-seal-handoff} and \autoref{thm:real-completion-exact-boundary-real-seal-nonescape}. The first theorem carries the same finite cofinal-tail route to Real and Completion consumers, and the second prevents the terminal $\RealUp(E)$ seal from bypassing the exact-boundary route. The excluded quotient, host-equality, selected-limit, choice, completeness, and bridge coordinates therefore cannot be inserted between the finite-tail-filter handoff and the accepted boundary read.
\end{proof}

\begin{theorem}[Real completion terminal-route pullback]
\label{thm:real-completion-exact-boundary-terminal-route-pullback}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the terminal $\RealUp(E)$ read is the pullback of the same displayed route
$$
\StreamNameUp(W),\quad \RegSeqRatUp(R),\quad \DyadicRatCoreUp(D)
$$
over the seal, classifier, witness-ledger, and budget rows $L,K,J,S$. If two accepted terminal reads display the same rows $L,K,J,S,W,R,D,H,C,P,N$, then completion-facing consumers cannot distinguish their $\RealUp$ terminal rows except through the displayed terminal coordinate of that finite packet. No quotient stream row, host real equality row, selected-limit row, countable-choice row, metric-completeness row, or bridge row participates in the pullback.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTerminalRoutePullback}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}. The terminal row $E$ is not a detached Real object; it appears only as the $\RealUp$ coordinate of the same finite packet that already displays $L,K,J,S,W,R,D,H,C,P,N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The NameCert obligations expose the seal, classifier, witness, budget, StreamName, RegSeqRat, DyadicRatCore, terminal Real, transport, replay, provenance, and naming rows as one carrier surface. Hence the displayed terminal read is determined at the completion boundary by the same route data, not by an external selector.

Apply \autoref{thm:real-completion-exact-boundary-streamname-regseq-route}. The route first reads $\StreamNameUp(W)$, then $\RegSeqRatUp(R)$, then $\DyadicRatCoreUp(D)$, and reaches $\RealUp(E)$ over $L,K,J,S$. This is the advertised pullback square at the consumer boundary: the terminal Real face is the fourth face attached to the preceding three displayed faces over the four governing rows.

Finally apply \autoref{thm:real-completion-exact-boundary-nonescape} and \autoref{thm:real-completion-exact-boundary-four-face-exactness}. Two accepted reads with the same displayed nonterminal route and the same structural rows can be compared only through the four-face inventory already exported by the packet. The theorem explicitly refuses quotient streams, host real equality, selected limits, countable choice, metric completeness, and bridge rows, so those absent objects cannot distinguish the two completion-facing reads.
\end{proof}

\begin{theorem}[Real completion terminal seal determinacy]
\label{thm:real-completion-exact-boundary-terminal-seal-determinacy}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
and
$$
B'=(L',K',J',S',W',R',D',E',H',C',P',N')
$$
be accepted $\RealCompletionExactBoundaryUp$ packets. Suppose the rows $L,K,J,S,W,R,D,H,C,P,N$ and $L',K',J',S',W',R',D',H',C',P',N'$ agree through the displayed componentwise $\hsame$ comparison, the displayed $\Cont$ replay, the displayed $\Pkg$ provenance row, and the local $\NameCert_{\RealCompletionExactBoundaryUp}$ comparison. Then every completion-facing consumer identifies the terminal $\RealUp$ rows $E$ and $E'$ only through the displayed terminal coordinate of the finite packets. No quotient stream, host real equality, selected limit, countable choice, metric-completeness row, ambient-completeness row, or bridge row can distinguish the two terminal seal reads.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTerminalSealDeterminacy}
\begin{proof}
Begin with \autoref{thm:real-completion-exact-boundary-terminal-route-pullback}. The terminal $\RealUp$ read in each accepted packet is pulled back over the same displayed StreamName, RegSeqRat, and DyadicRatCore route above the governing rows $L,K,J,S$.

Apply \autoref{thm:real-completion-exact-boundary-seal-budget-prefix-pullback}. The assumed comparison of the nonterminal rows is exactly the comparison admitted by the finite boundary: componentwise $\hsame$, continuation replay, package provenance, and the local NameCert row. Thus the two terminal reads meet over the same displayed prefix and structural tail, not over an external Real object.

Now use \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The only completion-facing and terminal Real faces exported after the prefix are $W,R,D,E$ in the first packet and $W',R',D',E'$ in the second packet. Since the first three faces are already part of the displayed comparison, the remaining terminal coordinate is the only place where a completion-facing consumer can read the Real seal.

Finally apply \autoref{thm:real-completion-exact-boundary-real-seal-nonescape}, \autoref{thm:real-completion-exact-boundary-nonescape}, and \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. These exclusions leave no quotient stream, host equality, selected-limit, choice, metric-completeness, ambient-completeness, or bridge coordinate with a carrier slot or insertion point. Hence any accepted consumer identifies $E$ and $E'$ only through the displayed terminal coordinate of the finite $\RealCompletionExactBoundaryUp$ packet.
\end{proof}

\begin{theorem}[Real completion seal-classifier witness balance]
\label{thm:real-completion-exact-boundary-seal-classifier-witness-balance}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. Any completion-facing consumer that reaches one of the four terminal faces
$$
\StreamNameUp(W),\quad \RegSeqRatUp(R),\quad \DyadicRatCoreUp(D),\quad \RealUp(E)
$$
must first display the seal and classifier rows $L,K$ and the witness-ledger and budget rows $J,S$ of the same packet. Thus the four terminal faces cannot be consumed from the boundary as a detached tail; they are read only after the local seal, classifier, witness, and budget rows have met inside the accepted NameCert carrier.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:real-completion-exact-boundary-carrier}. The rows $L,K,J,S$ occur before $W,R,D,E$ in the displayed packet, and the theorem concerns only consumers of that accepted finite carrier.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The NameCert obligations make $L$ the local seal row, $K$ the classifier row, $J$ the witness-ledger row, and $S$ the budget row of the same certificate surface. Hence a consumer that reads any later face of the carrier already has the four governing rows in scope.

Now use \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The completion and terminal Real faces exported by the boundary are exactly $W,R,D,E$ after the governing rows. Since the exactness theorem exposes no detached terminal tail, the four faces can be consumed only through the balanced seal, classifier, witness, and budget prefix.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundarySealClassifierWitnessBalance}

\begin{theorem}[Real completion exact-boundary seal-budget prefix pullback]
\label{thm:real-completion-exact-boundary-seal-budget-prefix-pullback}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. Any consumer route that reaches one of the four faces
$$
\StreamNameUp(W),\quad \RegSeqRatUp(R),\quad \DyadicRatCoreUp(D),\quad \RealUp(E)
$$
pulls back the same governing prefix $L,K,J,S$. The equality test for the four governing rows is only the displayed comparison through the componentwise $\hsame$ rows $H$, the displayed $\Cont$ replay $C$, the $\Pkg$ provenance row $P$, and the local $\NameCert_{\RealCompletionExactBoundaryUp}$ row $N$. It does not use quotient stream equality, host real equality, a selected limit, countable choice, metric completeness, ambient completeness, or a bridge coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundarySealBudgetPrefixPullback}
\begin{proof}
Project the carrier in \autoref{def:real-completion-exact-boundary-carrier}. The accepted packet lists $L,K,J,S$ before the four faces $W,R,D,E$, and the structural rows $H,C,P,N$ are the only displayed rows available for comparing that prefix across consumer reads.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. It identifies $L$ as the completion-seal row, $K$ as the classifier row, $J$ as the witness-ledger row, and $S$ as the synchronized budget row inside the same local NameCert surface. It also identifies $H,C,P,N$ as the componentwise transport, continuation replay, package provenance, and local naming rows for that surface.

Use \autoref{thm:real-completion-exact-boundary-seal-classifier-witness-balance} and \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The first theorem forces any consumer of the four later faces to display the governing prefix first, while the second theorem says that the only Real and completion faces behind that prefix are $W,R,D,E$.

Finally apply \autoref{thm:real-completion-exact-boundary-nonescape}. Since the accepted carrier has no quotient stream, host equality, selected-limit, choice, completeness, ambient-completeness, or bridge coordinate, none of those absent objects can alter the pullback of $L,K,J,S$ along any of the four displayed faces.
\end{proof}

\begin{theorem}[Real completion terminal consumer exactness]
\label{thm:real-completion-exact-boundary-terminal-consumer-exactness}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
every completion-facing consumer and every terminal $\RealUp$ consumer reads exactly the finite route
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
The route begins with the seal, classifier, witness-ledger, and budget rows, passes through the four completion and terminal faces $W,R,D,E$, and ends with the transport, continuation, package, and local naming rows $H,C,P,N$. No shorter route and no route with an added quotient, host-equality, selected-limit, choice, completeness, or bridge coordinate is a consumer route for the accepted boundary.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTerminalConsumerExactness}
\begin{proof}
Start from \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The accepted NameCert surface lists the rows $L,K,J,S,W,R,D,E,H,C,P,N$ as one finite carrier inventory, so a consumer route for the accepted boundary is a route through that inventory.

Apply \autoref{thm:real-completion-exact-boundary-seal-budget-prefix-pullback}. It pulls the first four governing rows back unchanged along the completion and Real faces and restricts their equality test to the displayed $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.

Next apply \autoref{thm:real-completion-exact-boundary-nonescape} and \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The non-escape theorem rules out external completion coordinates, while the four-face theorem identifies $W,R,D,E$ as the only completion-facing and terminal Real faces exported after $L,K,J,S$.

Use \autoref{thm:real-completion-exact-boundary-finite-tail-filter-handoff}. When the boundary is presented through a finite cofinal-tail filter, the same four faces pass through the finite-tail-filter handoff rather than through a separate completion route.

Finally apply \autoref{thm:real-completion-exact-boundary-terminal-route-pullback}. The terminal $\RealUp(E)$ read is pulled back over the same displayed route and the rows $H,C,P,N$ remain the trailing structural rows of the accepted packet. Therefore every completion-facing or terminal Real consumer has exactly the finite route displayed in the statement.
\end{proof}

\begin{theorem}[Real completion no completeness escape]
\label{thm:real-completion-exact-boundary-no-completeness-escape}
For an accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
there is no insertion point between the accepted boundary and the terminal $\RealUp(E)$ seal for a quotient stream, host real equality, selected limit, metric-completeness row, bridge row, or ambient completeness coordinate. Any such object lies outside the finite consumer route
$$
L,K,J,S,W,R,D,E,H,C,P,N
$$
and therefore cannot mediate terminal Real consumption for the accepted boundary.
\end{theorem}
\begin{proof}
Project the accepted packet and apply \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}. Terminal Real consumption is already fixed as the displayed finite route, so an added object would have to occupy a coordinate not present in the packet.

Apply \autoref{thm:real-completion-exact-boundary-nonescape} for quotient stream, host equality, selected-limit, choice, completeness, and bridge exclusions at the completion boundary. Apply \autoref{thm:real-completion-exact-boundary-real-seal-nonescape} for the terminal $\RealUp(E)$ seal.

It remains only to compare the consumer point where such an object might be inserted. By \autoref{thm:real-completion-exact-boundary-seal-classifier-witness-balance}, the governing rows $L,K,J,S$ must already meet before $W,R,D,E$ are consumed. By \autoref{thm:real-completion-exact-boundary-terminal-route-pullback}, the terminal Real face is the pullback of that same finite route. Hence quotient, equality, selected-limit, metric-completeness, bridge, and ambient-completeness coordinates have no packet-projection slot between the accepted boundary and the terminal Real seal.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryNoCompletenessEscape}

\begin{theorem}[Real completion roadmap off-table refusal]
\label{thm:real-completion-exact-boundary-roadmap-off-table-refusal}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the only accepted completion-facing and terminal Real route remains the finite
row list
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
Consequently the packet cannot be read as Real completeness, metric
completeness, trichotomy, open-cover compactness, sequential compactness,
Heine-Borel compactness, quotient-stream equality, host real equality, a
selected-limit principle, countable choice, or a standard bridge.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}.
It fixes every completion-facing or terminal Real consumer to the displayed
finite route $L,K,J,S,W,R,D,E,H,C,P,N$.

Next use \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The
only completion-facing and terminal Real faces exported by an accepted packet
are $\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and
$\RealUp(E)$, with no separate carrier for quotient streams, host equality,
selected limits, compactness, trichotomy, choice, or bridge data.

Now apply
\autoref{thm:real-completion-exact-boundary-terminal-normal-form-absorption}.
Even a certified terminal read through the finite-window and pullback normal
forms is absorbed back into the same four-face packet with structural rows
$H,C,P,N$; a second read adds no trichotomy, open-cover compactness, hidden
selector, completeness, choice, or bridge row.

Finally use
\autoref{thm:real-completion-exact-boundary-no-completeness-escape}. Since the
accepted boundary has no insertion point between the finite packet and the
terminal $\RealUp(E)$ seal, the classical completeness and compactness readings
listed in the statement are outside the route rather than latent consequences
of it.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryRoadmapOffTableRefusal}

\begin{theorem}[Real completion exact-boundary mature route]
\label{thm:real-completion-exact-boundary-mature-route}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
consumption by a Real-facing or completion-facing route has exactly the finite mature route
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
The seal and classifier rows are $L,K$, the witness and budget rows are $J,S$, the four Phase Real and Completion faces are $W,R,D,E$, and the structural rows are $H,C,P,N$. When the sibling finite-tail-filter packet supplies the cofinal-tail surface, this route factors through that handoff. It exports no quotient stream, host real equality, selected limit, countable choice, metric completeness, ambient completeness, or bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryMatureRoute}
\begin{proof}
Project the carrier in \autoref{def:real-completion-exact-boundary-carrier} and apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. These identify the accepted packet rows $L,K,J,S,W,R,D,E,H,C,P,N$ and assign the seal, classifier, witness-ledger, budget, four face, transport, continuation, package, and local naming roles inside one finite inventory.

Next apply \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The completion-facing and terminal Real coordinates of any accepted packet are exactly $W,R,D,E$, so the mature route cannot add a separate completion object or a second terminal Real face.

Use \autoref{thm:real-completion-exact-boundary-finite-tail-filter-handoff} for the sibling cofinal-tail surface. When that sibling supplies the finite-tail-filter presentation, the same rows factor through the handoff and no additional route coordinate is introduced.

Finally apply \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness} and \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The terminal consumer route is already the displayed finite row list, and quotient streams, host equality, selected limits, choice, completeness, and bridge rows have no carrier slot or insertion point. Hence the displayed route is the chapter's final finite consumer route.
\end{proof}

\begin{theorem}[Real completion exact-boundary tail cofinality schedule factorization]
\label{thm:real-completion-exact-boundary-tail-cofinality-schedule-factorization}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet, and let
$$
T=(E_T,W_T,D_T,R_T,L_T,H_T,C_T,P_T,N_T)
$$
be an accepted $\TailCofinalityScheduleUp$ packet through which the four faces $W,R,D,E$ are consumed. Then the combined Real-completion and schedule consumer factors through the single exact-boundary route
$$
L,K,J,S,W,R,D,E,H,C,P,N
$$
together with the schedule route
$$
E_T,W_T,D_T,R_T,L_T,H_T,C_T,P_T,N_T.
$$
The schedule is a consumer-side factor of the same four faces, not an added completion coordinate. The combined route exports no quotient stream, host real equality, selected limit, countable choice, ambient completeness, metric-completeness, hidden tail oracle, unbounded schedule, or machine bridge row.
\end{theorem}
\begin{proof}
Start with \autoref{thm:real-completion-exact-boundary-four-face-exactness}. It identifies $W,R,D,E$ as the only StreamName, RegSeqRat, DyadicRatCore, and terminal Real faces exported by the accepted boundary after the governing rows $L,K,J,S$.

Next apply \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness} and \autoref{thm:real-completion-exact-boundary-mature-route}. These place every Real-facing or completion-facing consumer on the exact-boundary route $L,K,J,S,W,R,D,E,H,C,P,N$ and rule out quotient streams, host equality, selected limits, choice, completeness, and bridge rows as route coordinates.

Now attach the accepted $\TailCofinalityScheduleUp$ packet. By \autoref{thm:tail-cofinality-schedule-regular-cauchy-completion-route}, every completion-facing seal read through the schedule consumes the ordered schedule rows $E_T,W_T,D_T,R_T,L_T$ before the completion seal is available.

Finally use \autoref{thm:tail-cofinality-schedule-shared-tail-budget-factorization}. The shared-tail budget is already a finite consumer-side factor through the schedule route and its structural rows $H_T,C_T,P_T,N_T$. Since the exact-boundary route has only the four faces $W,R,D,E$ available for the Real-completion handoff, the schedule can factor those faces only as a consumer of that route, not as a new completion coordinate or hidden tail source.
\end{proof}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTailCofinalityScheduleFactorization}

\begin{theorem}[Real completion exact-boundary cofinal terminal determinacy]
\label{thm:real-completion-exact-boundary-cofinal-terminal-determinacy}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
and
$$
B'=(L,K,J,S,W,R,D,E',H,C,P,N)
$$
be accepted $\RealCompletionExactBoundaryUp$ packets. Suppose both packets are consumed through the same displayed $\FiniteTailFilterUp$ packet and the same accepted $\TailCofinalityScheduleUp$ route
$$
T=(E_T,W_T,D_T,R_T,L_T,H_T,C_T,P_T,N_T).
$$
Then every completion-facing consumer and every terminal $\RealUp$ consumer identifies the terminal seals $\RealUp(E)$ and $\RealUp(E')$ only through the displayed cofinal schedule $T$ and the exact-boundary terminal coordinate of the finite packets. The comparison exports no quotient stream equality, host real equality, selected limit, countable choice, ambient completeness, metric-completeness, hidden tail oracle, or bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryCofinalTerminalDeterminacy}
\begin{proof}
Apply \autoref{thm:real-completion-exact-boundary-finite-tail-filter-handoff}. Since both accepted packets enter through the same displayed finite-tail filter, the cofinal-tail entry for $W,R,D,E$ and $W,R,D,E'$ is already the sibling handoff surface, not a separate completion coordinate.

Next apply \autoref{thm:real-completion-exact-boundary-tail-cofinality-schedule-factorization}. The shared schedule rows $E_T,W_T,D_T,R_T,L_T,H_T,C_T,P_T,N_T$ are therefore consumed as a finite consumer-side factor of the same exact-boundary route. They do not create a second terminal Real row and do not supply a hidden tail source.

Use \autoref{thm:real-completion-exact-boundary-terminal-route-pullback} and \autoref{thm:real-completion-exact-boundary-terminal-seal-determinacy}. The first binds each terminal $\RealUp$ row to the displayed StreamName, RegSeqRat, and DyadicRatCore route over $L,K,J,S$; the second says that matching nonterminal and structural rows leave the terminal coordinate as the only Real-seal read available to completion-facing consumers.

Finally apply \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The excluded quotient, host-equality, selected-limit, choice, completeness, hidden-tail, and bridge objects have no carrier slot in either packet and no insertion point in the shared schedule route. Thus any accepted consumer identifies the terminal seals only through the displayed cofinal schedule and the exact-boundary terminal coordinate.
\end{proof}

\begin{theorem}[Real completion exact-boundary obligation scope]
\label{thm:real-completion-exact-boundary-obligation-scope}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the $\RealCompletionExactBoundaryUp$ obligation scope is exactly the finite route containing the completion seal $L$, seal classifier $K$, witness ledger $J$, budget synchronizer $S$, $\StreamNameUp$ window $W$, $\RegSeqRatUp$ readback $R$, $\DyadicRatCoreUp$ tolerance row $D$, terminal $\RealUp$ seal $E$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert_{\RealCompletionExactBoundaryUp}$ row $N$. No quotient stream, host real equality, selected limit, countable-choice row, metric-completeness row, ambient-completeness coordinate, or bridge row belongs to that scope.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryObligationScope}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}. It displays exactly the packet rows $L,K,J,S,W,R,D,E,H,C,P,N$, with $H,C,P,N$ serving only as transport, replay, provenance, and local naming rows for that same packet.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The NameCert surface names each displayed row as an obligation of the accepted carrier, so the seal, classifier, witness-ledger, budget, StreamName, RegSeqRat, DyadicRatCore, terminal Real, transport, continuation, package, and local naming rows all lie inside the same finite route.

Next use \autoref{thm:real-completion-exact-boundary-four-face-exactness} and \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}. These bind the four Phase Real and Completion faces to the consumer route and prevent a shorter or enlarged terminal route from serving as the accepted boundary.

Finally apply \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The excluded quotient, host-equality, selected-limit, countable-choice, completeness, and bridge objects have no carrier slot and no consumer insertion point, so they are outside the obligation scope rather than dormant obligations of the packet.
\end{proof}

\begin{theorem}[Real completion exact-boundary scoped obligation closure]
\label{thm:real-completion-exact-boundary-scoped-obligation-closure}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the scoped obligation surface is exhausted by the seal row $L$, classifier row $K$, witness-ledger row $J$, synchronizer row $S$, $\StreamNameUp$ row $W$, $\RegSeqRatUp$ row $R$, $\DyadicRatCoreUp$ row $D$, terminal $\RealUp$ row $E$, componentwise $\hsame$ transports $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert_{\RealCompletionExactBoundaryUp}$ row $N$. No quotient stream, host real equality, selected limit, countable choice, metric-completeness, ambient-completeness, or bridge row is in scope.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryScopedObligationClosure}
\begin{proof}
Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. It identifies the accepted carrier surface with the displayed rows $L,K,J,S,W,R,D,E,H,C,P,N$ and gives each row its local NameCert role.

Next apply \autoref{thm:real-completion-exact-boundary-four-face-exactness}. The completion-facing faces $W,R,D,E$ are exactly the StreamName, RegSeqRat, DyadicRatCore, and terminal Real rows already present in that carrier surface, so there is no extra completion coordinate to add.

Use \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}. Terminal Real consumption follows the same finite route and leaves $H,C,P,N$ as the componentwise transport, continuation replay, package provenance, and local naming rows of the packet.

Finally apply \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. Quotient streams, host real equality, selected limits, countable choice, metric-completeness, ambient-completeness, and bridge rows have neither carrier slots nor consumer insertion points. Hence the displayed packet rows exhaust the scoped obligation surface.
\end{proof}

\begin{theorem}[Real completion exact-boundary public bridge factorization]
\label{thm:real-completion-exact-boundary-public-bridge-factorization}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
the public exact-boundary surface factors the four Phase Real and Completion
faces through the displayed packet $L,K,J,S,W,R,D,E,H,C,P,N$. The bridge is a
paper-side factorization only: it exports no quotient stream, host real
equality, selected limit, countable choice, ambient completeness,
metric-completeness, or machine bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryUp\_StdBridge}
\begin{proof}
First apply
\autoref{thm:real-completion-exact-boundary-scoped-obligation-closure}. It
places the accepted boundary on the finite route
$L,K,J,S,W,R,D,E,H,C,P,N$ and leaves no carrier slot outside those rows.

Next use \autoref{thm:real-completion-exact-boundary-four-face-exactness}.
The completion-facing and terminal Real faces are exactly the displayed
StreamName, RegSeqRat, DyadicRatCore, and Real rows $W,R,D,E$ inside the same
packet.

Now apply
\autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}. A
public consumer of the exact-boundary surface can reach those four faces only
through the seal, classifier, witness-ledger, synchronizer, transport,
continuation, package, and local naming rows already present in $B$.

Finally use
\autoref{thm:real-completion-exact-boundary-no-completeness-escape}. Quotient
streams, host real equality, selected limits, countable choice, ambient or
metric completeness, and machine bridge rows have no coordinate in the
displayed packet, so the factorization is a paper-side bridge and not a
checked machine bridge.
\end{proof}

\begin{theorem}[Real completion exact-boundary terminal consumer exhaustion]
\label{thm:real-completion-exact-boundary-four-face-terminal-consumer-exhaustion}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
every completion-facing or terminal Real consumer reads exactly the four Phase
Real and Completion faces $\StreamNameUp(W)$, $\RegSeqRatUp(R)$,
$\DyadicRatCoreUp(D)$, and $\RealUp(E)$. Those reads occur after the governing
rows $L,K,J,S$ and through the structural rows $H,C,P,N$. No quotient stream,
host real equality, selected limit, countable-choice row, metric-completeness
row, ambient-completeness row, or bridge row participates in the consumer
surface.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryFourFaceTerminalConsumerExhaustion}
\begin{proof}
Project the carrier of \autoref{def:real-completion-exact-boundary-carrier}.
It displays the accepted packet as the finite row list
$L,K,J,S,W,R,D,E,H,C,P,N$, so a consumer has no coordinate outside the
displayed carrier.

Apply
\autoref{thm:real-completion-exact-boundary-namecert-obligations} and
\autoref{thm:real-completion-exact-boundary-streamname-regseq-route}. The
NameCert obligations bind the governing rows $L,K,J,S$, and the displayed
route carries StreamName and RegSeqRat consumption into the later completion
faces.

Next use \autoref{thm:real-completion-exact-boundary-four-face-exactness} and
\autoref{thm:real-completion-exact-boundary-terminal-route-pullback}. These
identify $\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and
$\RealUp(E)$ as the exact four completion-facing faces, with the terminal Real
read pulled back over the same finite route.

Finally apply
\autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness} and
\autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The first
theorem makes every completion-facing or terminal Real consumer pass through
$L,K,J,S,W,R,D,E,H,C,P,N$, while the second rules out quotient streams, host
real equality, selected limits, countable choice, metric completeness, ambient
completeness, and bridge rows as carrier slots or insertion points. Hence the
four displayed faces exhaust the terminal consumer surface.
\end{proof}

\begin{theorem}[Real completion exact-boundary terminal normal-form absorption]
\label{thm:real-completion-exact-boundary-terminal-normal-form-absorption}
For every accepted $\RealCompletionExactBoundaryUp$ packet
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N),
$$
consider a certified terminal read which first passes through the
$\StreamNameUp(W)$ finite-window normal form, then through the
$\RegularCauchyLimitClassifierUp$ finite pullback route over the displayed
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and finally through
the exact-boundary consumer surface of $B$. The composite read is absorbed by
the same four-face packet
$$
W,R,D,E
$$
with structural rows $H,C,P,N$.

Applying the same terminal read a second time adds no quotient stream equality,
host real equality, selected limit, countable-choice row, ambient completeness
row, metric-completeness row, bridge row, trichotomy row, open-cover
compactness row, or hidden tail selector.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTerminalNormalFormAbsorption}
\begin{proof}
First put the terminal read in StreamName normal form. By
\autoref{thm:streamname-terminal-pullback-idempotence}, once the finite-window
read exposes the displayed StreamName, DyadicRatCore, RegSeqRat, Real, and
support rows, a further terminal pullback reads the same finite packet.

Next transport that normal form through the classifier. Apply
\autoref{thm:regular-cauchy-limit-classifier-budgeted-seal-pullback}. The
classifier handoff remains on the finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$,
and $\NameCert$ route and exports no quotient stream, host real equality,
selected limit, hidden selector, unbounded schedule, or ambient completeness
coordinate.

Now enter the exact-boundary surface. By
\autoref{thm:real-completion-exact-boundary-four-face-terminal-consumer-exhaustion},
every completion-facing or terminal Real consumer of $B$ reads exactly
$\StreamNameUp(W)$, $\RegSeqRatUp(R)$, $\DyadicRatCoreUp(D)$, and $\RealUp(E)$
through the structural rows $H,C,P,N$.

Finally apply
\autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The
off-table coordinates named above have no carrier slots or consumer insertion
points in $B$, so the second terminal read is absorbed by the same four-face
packet rather than producing a new equality, choice, completeness, bridge,
trichotomy, compactness, or tail-selection row.
\end{proof}

\begin{theorem}[Real completion exact-boundary all rows necessary]
\label{thm:real-completion-exact-boundary-all-rows-necessary}
For every accepted $\RealCompletionExactBoundaryUp$ read, validity is exactly
the display of the carrier rows
$$
L,K,J,S,W,R,D,E,H,C,P,N.
$$
Deleting or replacing any seal, classifier, witness, or budget row $L,K,J,S$;
any four-face row $W,R,D,E$; or any support row $H,C,P,N$ leaves the
exact-boundary carrier. In particular, no quotient stream, host real equality,
selected limit, countable choice, metric completeness, ambient completeness,
bridge row, or aggregate formalstatus row can substitute for a missing
displayed row.
\end{theorem}
\leanchecked{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryAllRowsNecessary}
\begin{proof}
Start from
\autoref{thm:real-completion-exact-boundary-namecert-obligations}. The
NameCert surface names the accepted carrier only as the finite inventory
$L,K,J,S,W,R,D,E,H,C,P,N$, so the seal row, classifier row, witness ledger,
and synchronizer are not optional parameters of a larger completion object.

Next apply
\autoref{thm:real-completion-exact-boundary-four-face-exactness}. The
completion and terminal Real faces are exactly $W,R,D,E$ after $L,K,J,S$.
Removing or replacing any one of these rows destroys the displayed four-face
boundary rather than producing a second accepted face.

Now use
\autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness} and
\autoref{thm:real-completion-exact-boundary-terminal-normal-form-absorption}.
Every completion-facing and terminal consumer reads the whole finite route,
and repeated terminal normal-form reading is absorbed by the same four-face
packet with the same support rows $H,C,P,N$. Thus the transport,
continuation, provenance, and local naming rows are necessary support for the
accepted read.

Finally apply
\autoref{thm:real-completion-exact-boundary-nonescape}. Quotient streams, host
real equality, selected limits, countable choice, metric completeness, ambient
completeness, bridge rows, and aggregate formalstatus rows have no carrier
slot and no consumer insertion point. Replacing any displayed row by one of
those objects therefore leaves the exact-boundary packet rather than giving a
different valid read.
\end{proof}

\closureat{RealCompletionExactBoundaryUp}{scopedStr}[BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTasteGate\_single\_carrier\_alignment]
\closureat{RealCompletionExactBoundaryUp}{publicStr}[BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTasteGate\_single\_carrier\_alignment]
\closureat{RealCompletionExactBoundaryUp}{bridgedStr}[BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTasteGate\_single\_carrier\_alignment]
\closureat{RealCompletionExactBoundaryUp}{matureStr}[BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\RealCompletionExactBoundaryUp}
  \constructivestory{A $\RealCompletionExactBoundaryUp$ packet is generated from displayed seal, classifier, witness-ledger, synchronizer, StreamName, RegSeqRat, DyadicRatCore, terminal Real, transport, continuation, package, and local naming rows.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:real-completion-exact-boundary-mature-route} closes the concrete Real-completion finite route through $L,K,J,S,W,R,D,E,H,C,P,N$, and the displayed carrier keeps the TasteGate boundary on the same finite packet.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.RealCompletionExactBoundaryUp.RealCompletionExactBoundaryUp\_StdBridge}
  \leandef{BEDC.Derived.RealCompletionExactBoundaryUp.taste\_gate}
  \bridgestatus{bridgeChecked}
  \origin{ai}
  \notclaimed{This chapter does not close quotient stream equality, host real equality, selected limits, countable choice, ambient completeness, or metric completeness.}
  \upgradepath{No further upgrade -- chapter at the top of the formal axis.}
\end{closurestatus}

The Lean TasteGate file at \texttt{lean4/BEDC/Derived/RealCompletionExactBoundaryUp/TasteGate.lean} supplies $\mathsf{Nontrivial}\ \RealCompletionExactBoundaryUp$ and $\mathsf{FieldFaithful}\ \RealCompletionExactBoundaryUp$ instances for the displayed finite carrier; bridge checking remains governed by the verification axis.

\begin{lemma}[Real completion exact-boundary forgetful projection]
\label{lem:real-completion-exact-boundary-forgetful-projection}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. The displayed boundary admits the finite target projection
$$
\operatorname{Forget}_{\mathrm{target}}(B)=(E,K,J,N),
$$
where $E$ is the terminal $\RealUp$ target row, $K$ is the displayed completion-seal classifier row, $J$ is the displayed witness-ledger row, and $N$ is the local $\NameCert_{\RealCompletionExactBoundaryUp}$ row. This projection is exact for target-facing reads: every accepted consumer that asks only for the target row, classifier row, ledger row, and local NameCert row factors through $(E,K,J,N)$, while any accepted read that distinguishes two packets with the same $(E,K,J,N)$ must inspect one of the dropped rows $L,S,W,R,D,H,C,P$ and is therefore not a read of the target projection. No quotient stream row, host real equality row, selected-limit row, countable-choice row, ambient-completeness row, metric-completeness row, or machine row is exported by this projection.
\end{lemma}
\begin{proof}
Project the accepted carrier through \autoref{def:real-completion-exact-boundary-carrier}. The displayed packet has exactly the rows $L,K,J,S,W,R,D,E,H,C,P,N$. Among them, the terminal target coordinate is $E$, the classifier coordinate is $K$, the witness-ledger coordinate is $J$, and the local naming coordinate is $N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. It identifies the same finite row inventory as the local $\NameCert_{\RealCompletionExactBoundaryUp}$ surface: $K$ is read as classifier exposure, $J$ as witness-ledger exposure, $E$ as terminal $\RealUp$ seal exposure, and $N$ as local naming. The remaining rows $L,S,W,R,D,H,C,P$ are respectively seal, synchronizer, finite-window, readback, dyadic-tolerance, transport, replay, and provenance support for the full boundary.

Thus the target projection is obtained by dropping exactly the support rows and retaining $(E,K,J,N)$. A consumer whose request is restricted to target, classifier, ledger, and local NameCert data has no coordinate in that request for $L,S,W,R,D,H,C,P$, so its read factors through the displayed four-row projection.

It remains to rule out hidden coordinates. By \autoref{thm:real-completion-exact-boundary-nonescape}, every accepted consumer of the full boundary factors through the displayed finite route and receives no quotient stream equality, host real equality, hidden selector, second seal route, detached witness ledger, or ambient completeness coordinate. By \autoref{thm:real-completion-exact-boundary-no-completeness-escape}, there is also no insertion point for selected limits, metric completeness, or a machine row between the accepted boundary and the terminal $\RealUp(E)$ seal. Therefore two accepted packets with the same $(E,K,J,N)$ can be distinguished only by inspecting one of the dropped displayed support rows, which is outside the target projection, or by asking for an absent ambient coordinate, which is not exported by the packet.
\end{proof}

\begin{theorem}[Real completion exact-boundary substrate relation boundary]
\label{thm:real-completion-exact-boundary-substrate-relation-boundary}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. Any reading of this packet into a Rule~110, cellular, binary, $\mathsf{FKernel}$, or $\BHist$ substrate must be a typed relation certificate over the displayed rows
$$
L,K,J,S,W,R,D,E,H,C,P,N,
$$
with relation kind one of bisimulation, row embedding, or substrate mirror. It cannot be a definitional equality between the Real-completion boundary and the chosen substrate. The source side of the certificate is the displayed Real-completion route, the target side is the named substrate read, and the direction is fixed by the consumer route from the seal, classifier, witness-ledger, and budget rows through $W,R,D,E$ to $H,C,P,N$. Any certificate that uses an unlisted host coordinate, unlisted source coordinate, quotient stream equality, host real equality, selected limit, countable choice, metric-completeness, ambient-completeness, or machine bridge row is not a certificate for the accepted boundary. Any displayed row among $L,K,J,S,W,R,D,E,H,C,P,N$ that is needed by that relation remains named in the certificate and is not eliminated by the substrate interpretation.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:real-completion-exact-boundary-carrier}. Its full displayed inventory is exactly the seal row $L$, classifier row $K$, witness-ledger row $J$, synchronizer row $S$, StreamName finite-window row $W$, RegSeqRat readback row $R$, DyadicRatCore tolerance row $D$, terminal Real seal row $E$, componentwise transport row $H$, continuation replay row $C$, package provenance row $P$, and local naming row $N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The local NameCert surface exposes those rows as one finite packet and exposes no coordinate for quotient stream equality, host real equality, hidden selection, a second seal route, detached witness evidence, or ambient completeness. Hence a substrate-facing read has no object from which to form a definitional equality with a Rule~110, cellular, binary, $\mathsf{FKernel}$, or external $\BHist$ substrate.

Use \autoref{thm:real-completion-exact-boundary-streamname-regseq-route} and \autoref{thm:real-completion-exact-boundary-seal-classifier-witness-balance}. They force the consumer direction: the rows $L,K,J,S$ govern the route, the rows $W,R,D,E$ are the visible completion and terminal faces, and the rows $H,C,P,N$ transport, replay, package, and name that same route. Thus the only admissible substrate comparison is relational data attached to this route. If the comparison is symmetric behavioral matching, it is a bisimulation; if it injects the displayed route rows into a substrate ledger, it is a row embedding; if it interprets the same visible route in the substrate vocabulary without identifying carriers, it is a substrate mirror.

Finally apply \autoref{thm:real-completion-exact-boundary-scoped-obligation-closure} and \autoref{thm:real-completion-exact-boundary-no-completeness-escape}. The scoped obligation surface is exhausted by $L,K,J,S,W,R,D,E,H,C,P,N$, and the excluded host, equality, selection, choice, completeness, and machine rows have no carrier slot or insertion point. Therefore every accepted substrate relation certificate must be read from the displayed rows, every unlisted coordinate is rejected, and every noneliminable displayed row remains named at the boundary rather than being collapsed into definitional equality.
\end{proof}

\begin{theorem}[Real completion exact-boundary left-right mirror boundary]
\label{thm:real-completion-exact-boundary-left-right-mirror-boundary}
Let
$$
B=(L,K,J,S,W,R,D,E,H,C,P,N)
$$
be an accepted $\RealCompletionExactBoundaryUp$ packet. A proposed left-right mirror read of this boundary is accepted only in the following rowwise sense: its source side is the displayed Real-completion route
$$
L,K,J,S,W,R,D,E,H,C,P,N,
$$
and its target side is an interpretation of exactly the same named history, observation, result, termination, provenance, and certificate rows. Thus the mirror has no independent right-side seal, no independent right-side witness ledger, no second terminal Real row, and no separate right-side certificate row. If a proposed counterpart is obtained by renaming the displayed rows while preserving the roles of $L,K,J,S,W,R,D,E,H,C,P,N$, it is only a substrate-mirror interpretation of the same packet; if it requires any unlisted right-side row, then the asymmetry is a boundary condition rather than an accepted counterpart.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:real-completion-exact-boundary-carrier}. The carrier exposes exactly the rows $L,K,J,S,W,R,D,E,H,C,P,N$: the completion seal $L$, seal classifier $K$, witness ledger $J$, synchronizer $S$, StreamName window $W$, RegSeqRat readback $R$, DyadicRatCore tolerance row $D$, terminal $\RealUp$ seal $E$, componentwise transport $H$, displayed $\Cont$ replay $C$, package provenance $P$, and local $\NameCert_{\RealCompletionExactBoundaryUp}$ row $N$.

Apply \autoref{thm:real-completion-exact-boundary-namecert-obligations}. The local NameCert surface consists exactly of those rows. In particular, the seal and classifier side $L,K$ and the witness and budget side $J,S$ are not two independent boundary objects; they are governing rows of the same displayed packet, and the later rows $W,R,D,E$ are consumed only inside that packet.

Now use \autoref{thm:real-completion-exact-boundary-terminal-consumer-exactness}. Every completion-facing or terminal $\RealUp$ consumer reads exactly the finite route $L,K,J,S,W,R,D,E,H,C,P,N$. Therefore a mirror read cannot add a right-side history row, a right-side observation row, a second result row, a second terminal row, or a separate certificate row without leaving the accepted consumer route.

Finally apply \autoref{thm:real-completion-exact-boundary-substrate-relation-boundary}. A substrate mirror is permitted only as typed relation data over the displayed rows, with source side, target side, and direction fixed by the consumer route; it is not a definitional equality with a second carrier. Together with \autoref{thm:real-completion-exact-boundary-nonescape} and \autoref{thm:real-completion-exact-boundary-no-completeness-escape}, this excludes quotient stream equality, host real equality, selected limits, countable choice, metric completeness, ambient completeness, machine coordinates, and unlisted source or target coordinates. Hence the only accepted left-right mirror is the row-preserving interpretation of the same finite packet, and any stronger right-side counterpart is recorded as the exact-boundary asymmetry.
\end{proof}
