\chapter{A Concrete Naming Certificate for $\FastCauchyModulusUp$}
\label{ch:concrete-instances-fast-cauchy-modulus-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\FastCauchyModulusUp$ packet records the fast-threshold discipline that turns an ordinary Cauchy modulus into the doubled-window schedule expected by regular Cauchy and real-name consumers. It sits over the generic modulus schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives downstream RealCauchyModulus and RegSeqRat consumers one visible fast-modulus carrier before any Real or Completion route reads a seal.

\begin{definition}[Fast Cauchy modulus carrier]
\label{def:fast-cauchy-modulus-carrier}
A $\FastCauchyModulusUp$ carrier is a finite $\BHist$ packet
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source $\CauchyModulusUp$ row, read as a finite threshold schedule for Cauchy observations.
\item $F$ is the fast or doubled threshold discipline. It records, for each displayed precision request, whether the carrier uses the direct fast threshold or the doubled-window threshold, and it stores the comparison row showing that the selected threshold is strong enough for the requested tail estimate.
\item $S$ is the $\StreamNameUp$ finite-window row opened at the threshold selected by $F$ from $M$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger consumed by the selected window and by the regularity check.
\item $Q$ is the precision-query row whose dyadic request is read jointly by $M,F,S,D$.
\item $E$ is the $\RegSeqRatUp$ and $\RealUp$ handoff row exposed only after $M,F,S,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source modulus, fast discipline, stream window, dyadic ledger, precision query, handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a precision request through $M,F,S,D,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FastCauchyModulusUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FastCauchyModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,F,S,D,Q,E,H,C,P,N$. It has no coordinate for quotient stream equality, host real equality, countable choice, trichotomy, selected limits, unbounded stream reads, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.FastCauchyModulusUp.FastCauchyModulusUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Fast Cauchy modulus doubling window]
\label{thm:fast-cauchy-modulus-doubling-window}
Let
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N)
$$
be an accepted $\FastCauchyModulusUp$ carrier. Every regular-Cauchy or Real-facing consumer that requests a precision row $Q$ must read the finite route
$$
Q \longmapsto M,F \longmapsto S,D \longmapsto E \longmapsto H,C,P,N .
$$
If $F$ selects the direct fast threshold, the opened window $S$ is already the thresholded finite window supplied by $M$. If $F$ selects the doubled threshold, $S$ is the displayed enlarged window and $D$ records the dyadic slack showing that the doubled read implies the requested tail estimate. In both cases the consumer receives no unbounded stream read, quotient stream equality, host real equality, countable-choice schedule, trichotomy principle, selected limit, ambient $\RealUp$ completeness theorem, Lean verification, or bridge data.
\end{theorem}
\begin{proof}
Project the accepted carrier. The precision query $Q$ can reach a stream window only through the displayed source modulus row $M$ and the fast discipline row $F$, so the carrier exposes no separate threshold selector.

For the direct fast case, $F$ records that the threshold read from $M$ already satisfies the requested tail estimate. The window row $S$ is therefore the finite StreamName window opened at that threshold, and the dyadic ledger $D$ only records the requested tolerance account.

For the doubled case, $F$ records the doubled threshold before any window is opened. The row $S$ contains that enlarged finite window, and $D$ stores the dyadic slack proving that the doubled read is strong enough for the original precision request.

Finally $E,H,C,P,N$ hand the same displayed route to regular-Cauchy and Real-facing consumers. Since the excluded objects are absent from the carrier, no consumer can bypass the finite threshold-window-ledger path.
\end{proof}

\begin{theorem}[Fast Cauchy modulus NameCert obligations]
\label{thm:fast-cauchy-modulus-namecert-obligations}
For every accepted $\FastCauchyModulusUp$ carrier
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\FastCauchyModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source $\CauchyModulusUp$ row, fast threshold discipline, $\StreamNameUp$ finite window, $\DyadicRatCoreUp$ tolerance ledger, precision query, $\RegSeqRatUp$ and $\RealUp$ handoff, transport, replay, provenance, and local naming rows;
\item threshold exactness, requiring $F$ to select either the direct fast threshold or the doubled-window threshold from the displayed source modulus row $M$ for the same precision query $Q$;
\item finite-window exactness, requiring $S$ to be precisely the finite StreamName window opened by the threshold selected in $F$;
\item dyadic slack exactness, requiring $D$ to store the tolerance and slack row that makes the selected threshold sufficient for the requested tail estimate;
\item regular and Real handoff, requiring $E$ to consume $M,F,S,D,Q$ before exposing any $\RegSeqRatUp$ readback or $\RealUp$ seal;
\item componentwise transport, displayed replay, provenance, and local naming for the same displayed rows through $H,C,P,N$;
\item refusal of quotient stream equality, host real equality, countable choice, trichotomy, selected limits, unbounded stream reads, ambient $\RealUp$ completeness, Lean verification, and bridge checking as local certificate data.
\end{enumerate}
No Fast Cauchy modulus obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.FastCauchyModulusUp.FastCauchyModulusTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:fast-cauchy-modulus-carrier}. The visible packet consists exactly of the source modulus, fast threshold discipline, finite window, dyadic ledger, precision query, handoff, and structural rows.

Threshold exactness is finite precision induction on the displayed query row. At the base precision, $F$ records the selected threshold directly from $M$; at the next displayed precision, the same row either preserves the fast threshold discipline or opens the doubled threshold together with its comparison row.

Finite-window exactness follows by reading $S$ only after $F$ has selected the threshold. The induction step transports the selected threshold into the StreamName window, and the dyadic ledger $D$ records the slack needed to interpret that finite window at the requested precision.

The handoff row $E$ is downstream of $M,F,S,D,Q$, so regular-rational and Real consumers see only the displayed finite route. Componentwise $\hsame$ transport and displayed $\Cont$ replay preserve each coordinate through $H$ and $C$, and $P,N$ record the same carrier as package provenance and local name.

The excluded objects have no carrier coordinate. Therefore the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Fast Cauchy modulus threshold dichotomy]
\label{thm:fast-cauchy-modulus-threshold-dichotomy}
Let
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N)
$$
be an accepted $\FastCauchyModulusUp$ carrier. For the displayed precision query $Q$, the threshold discipline row $F$ exposes exactly one of the following rows read from the same source modulus row $M$: the direct fast threshold row, or the doubled-window threshold row. The choice is part of $F$ itself and is not supplied by a hidden selector, quotient stream equality, selected limit, countable choice, trichotomy, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge datum.
\end{theorem}
\begin{proof}
Project the accepted carrier using \autoref{def:fast-cauchy-modulus-carrier}. The only coordinates that mention thresholds are the source modulus row $M$, the fast discipline row $F$, and the precision query row $Q$.

Apply \autoref{thm:fast-cauchy-modulus-doubling-window}. A consumer can open a StreamName window only after $Q$ has passed through $M$ and $F$, and $F$ records whether the direct fast threshold or the doubled threshold is used.

Apply \autoref{thm:fast-cauchy-modulus-namecert-obligations}. Its threshold exactness row requires the selected threshold to be either the direct fast threshold or the doubled-window threshold from $M$ for the same $Q$. Since no other selector is present in the carrier, the two alternatives are exclusive and exhaustive on accepted packets.
\end{proof}

\begin{theorem}[Fast Cauchy modulus window exactness]
\label{thm:fast-cauchy-modulus-window-exactness}
Let
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N)
$$
be an accepted $\FastCauchyModulusUp$ carrier. The $\StreamNameUp$ finite window row $S$ and the $\DyadicRatCoreUp$ ledger row $D$ are determined by the threshold selected in $F$ for the precision query $Q$. If $F$ selects the direct fast threshold, then $S$ is the finite window opened at that threshold and $D$ records the requested tolerance account. If $F$ selects the doubled-window threshold, then $S$ is the enlarged finite window and $D$ records the dyadic slack proving that the doubled read preserves the requested tail estimate.
\end{theorem}
\begin{proof}
Project the carrier and read the route displayed in \autoref{thm:fast-cauchy-modulus-doubling-window}. The row $S$ appears only after the source modulus and threshold discipline rows have been read, so it is opened at the threshold selected in $F$.

In the direct case, the threshold stored by $F$ already supplies the requested tail estimate. Thus the StreamName row is the finite window at that threshold, and the DyadicRatCore row stores the tolerance ledger consumed by that read.

In the doubled case, $F$ stores the enlarged threshold before $S$ is opened. The same theorem identifies $S$ as the enlarged finite window and identifies $D$ as the dyadic slack ledger that transports the doubled read back to the original precision request.

The NameCert obligations of \autoref{thm:fast-cauchy-modulus-namecert-obligations} state that finite-window exactness and dyadic slack exactness are stored in those same displayed rows. No further window or tolerance coordinate is available.
\end{proof}

\begin{theorem}[Fast Cauchy modulus handoff nonescape]
\label{thm:fast-cauchy-modulus-handoff-nonescape}
Let
$$
M_{\mathrm{fast}}=(M,F,S,D,Q,E,H,C,P,N)
$$
be an accepted $\FastCauchyModulusUp$ carrier. Any $\RegSeqRatUp$ or $\RealUp$ handoff row $E$ must consume the displayed rows $M,F,S,D,Q$ before exposing a regular-rational readback or Real seal. The handoff exports no quotient stream equality, selected limit, countable-choice schedule, trichotomy principle, ambient $\RealUp$ completeness theorem, host real equality, Lean verification row, or bridge datum.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:fast-cauchy-modulus-carrier}. The handoff coordinate $E$ is listed downstream of the source modulus, threshold discipline, finite window, dyadic ledger, and precision query rows.

Apply \autoref{thm:fast-cauchy-modulus-doubling-window}. Every regular-Cauchy or Real-facing consumer follows the finite route through $Q$, then $M,F$, then $S,D$, and only then reaches $E$.

Apply \autoref{thm:fast-cauchy-modulus-namecert-obligations}. Its regular and Real handoff row requires $E$ to consume $M,F,S,D,Q$ before any readback or seal is exposed, while its refusal row excludes quotient stream equality, selected limits, choice, trichotomy, ambient completeness, Lean verification, and bridge data from the local certificate surface.

Therefore the handoff cannot escape the displayed fast-modulus route. It exposes only the readback or seal certified by the finite carrier rows.
\end{proof}

\falsifiablePrediction{Every $\FastCauchyModulusUp$ precision read factors through one CauchyModulus row, one fast or doubled threshold discipline row, one StreamName finite window, one DyadicRatCore tolerance ledger, one precision query, one RegSeqRat and RealUp handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchymodulus, streamname, dyadicratcore, regseqrat, real: $\FastCauchyModulusUp$ is not bijective to any listed sibling because it jointly carries the source modulus row, the fast or doubled threshold choice, the opened finite window, the dyadic slack ledger, and the regular-rational or Real-facing handoff as one certificate.}

\closureat{FastCauchyModulusUp}{seedStr}

\begin{closurestatus}{\FastCauchyModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fast-cauchy-modulus-carrier}, \autoref{thm:fast-cauchy-modulus-doubling-window}, and \autoref{thm:fast-cauchy-modulus-namecert-obligations} seed the finite fast-modulus route from a displayed CauchyModulus row through fast or doubled threshold discipline, StreamName finite window, DyadicRatCore tolerance ledger, precision query, RegSeqRat and Real handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient stream equality, host real equality, countable choice, trichotomy, selected limits, unbounded stream reads, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, threshold exactness, finite-window exactness, dyadic slack exactness, regular and Real handoff, componentwise transport, displayed replay, provenance, and finite consumer factorization for BEDC.Derived.FastCauchyModulusUp.}
  \constructivestory{A $\FastCauchyModulusUp$ packet is generated from one CauchyModulus row, one fast or doubled threshold discipline row, one StreamName finite window, one DyadicRatCore tolerance ledger, one precision query, one RegSeqRat and RealUp handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
