\chapter{A Concrete Naming Certificate for $\ContextFreeGrammarUp$}
\label{ch:concrete-instances-contextfreegrammar-namecert}
\origin{human}

The $\ContextFreeGrammarUp$ interface names a context-free grammar through a
finite grammar packet rather than through a host language set. In the
Hopcroft--Ullman presentation, a context-free grammar is given by a finite
terminal alphabet, finite nonterminal carrier, start symbol, and finite
production relation; here each of those rows is displayed as finite
$\mathsf{BHist}$ data with $\ListUp$ word rows and explicit provenance toward
$\RegularLanguageUp$ and $\TuringMachineUp$ consumers.

The yield and bridge boundary is consumed by \autoref{ch:concrete-instances-regularlanguage-namecert} for regular-language comparison and by \autoref{ch:concrete-instances-turingmachine-namecert} for machine-recognizer boundary checks. Thus the grammar packet is read as a finite sibling surface in the language-recognition lattice, not only as a kernel-local carrier.

\begin{definition}[ContextFreeGrammar BHist carrier]
\label{def:contextfreegrammar-bhist-carrier}
A $\ContextFreeGrammarUp$ packet is a finite record
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
with the following displayed rows:
\begin{enumerate}
\item $\Sigma$ is the terminal alphabet row, exposed as finite
  $\mathsf{BHist}$ data;
\item $N$ is the nonterminal carrier row, disjoint from the terminal rows by
  the displayed classifier surface;
\item $S$ is the start nonterminal row inside $N$;
\item $P$ is the finite production ledger, whose rows have one nonterminal
  left side and a $\ListUp$ right side over terminal and nonterminal symbols;
\item $w$ is the terminal yield word, displayed as a $\ListUp$ row over
  $\Sigma$;
\item $d$ is the finite derivation ledger, beginning at $S$ and replacing one
  displayed nonterminal occurrence by a row of $P$ at each step;
\item $y$ is the readback row identifying the terminal fringe of the final
  sentential form with the word row $w$;
\item $h$ stores componentwise $\hsame$ transports for alphabets,
  nonterminals, production rows, sentential forms, derivation rows, and yield
  rows;
\item $c$ stores the $\Cont$ routes for reading a production row and
  continuing along the finite derivation ledger;
\item $p$ stores $\Pkg$ provenance naming $\ListUp$, $\RegularLanguageUp$, and
  $\TuringMachineUp$ consumer surfaces;
\item $n$ is the local $\NameCert_{\ContextFreeGrammarUp}$ registration row.
\end{enumerate}
The carrier predicate is
$\mathsf{ContextFreeGrammarPacket}(G)$. It exports only the displayed finite
grammar, production, derivation, yield, transport, continuation, provenance,
and local naming rows.
\end{definition}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ContextFreeGrammar production stability]
\label{thm:contextfreegrammar-production-stability}
If two accepted $\ContextFreeGrammarUp$ packets classify together by the
displayed $\hsame$ rows, then every production row of the first packet
transports to exactly one production row of the second packet with transported
left nonterminal and transported $\ListUp$ right side. The transport preserves
terminal and nonterminal tags and introduces no host grammar relation.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_production\_stability}
\begin{proof}
Project the packets through
\autoref{def:contextfreegrammar-bhist-carrier}. A production row is a visible
entry of the finite ledger $P$ with one nonterminal left side and one displayed
right-side word.

Use the componentwise $\hsame$ rows in $h$ to transport the left nonterminal,
the terminal and nonterminal tags, and the $\ListUp$ right side. The $\Cont$
route in $c$ records that the transported row is read as the same production
position in the target packet.

The reverse read is the same finite ledger projection in the second packet.
Since the carrier has no coordinate for a host production relation, only the
displayed production rows can be transported.
\end{proof}

\begin{theorem}[ContextFreeGrammar derivation concatenation]
\label{thm:contextfreegrammar-derivation-concatenation}
For an accepted $\ContextFreeGrammarUp$ packet, two derivation ledger segments
whose endpoint and start sentential forms agree by a displayed $\hsame$ row
concatenate to a finite derivation ledger over the same production rows. The
concatenated ledger preserves the $\ListUp$ sentential-form rows,
$\mathsf{BHist}$ production witnesses, $\Cont$ routes, and $\Pkg$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_derivation\_concatenation}
\begin{proof}
Read the two finite derivation segments from the $d$ coordinate of
\autoref{def:contextfreegrammar-bhist-carrier}. The connecting hypothesis
identifies the terminal segment endpoint and the next segment start through a
displayed sentential-form transport row.

Append the second ledger after the first. Each step still reads a production
row of $P$, so \autoref{thm:contextfreegrammar-production-stability}
transports the production witnesses along the same packet classifier when
needed.

The composed $\Cont$ route first consumes the first segment and then the
second segment. All rows remain inside the finite carrier, so no infinite
derivation tree or host closure operation is introduced.
\end{proof}

\begin{theorem}[ContextFreeGrammar yield readback]
\label{thm:contextfreegrammar-yield-readback}
Every accepted terminal yield read of a $\ContextFreeGrammarUp$ packet factors
through the displayed start row $S$, the finite production ledger $P$, the
finite derivation ledger $d$, and the $\ListUp$ terminal word row $w$.
Conversely, a finite derivation ledger ending in a terminal sentential form
with readback row $y$ repacks as an accepted yield read of the same packet.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_yield\_readback}
\begin{proof}
For the forward direction, project the carrier rows. The yield coordinate is
the readback row $y$, and it is attached to the final sentential form of the
finite derivation ledger $d$.

Use \autoref{thm:contextfreegrammar-production-stability} at each derivation
step to keep the production witness inside the displayed ledger. The terminal
fringe is then read as the $\ListUp$ word row $w$ through the stored
continuation route.

For the reverse direction, start with a derivation ledger whose final form has
the displayed terminal readback row. These are exactly the carrier coordinates
$S$, $P$, $d$, $y$, and $w$, so they repack as the accepted yield read.
\end{proof}

\begin{theorem}[ContextFreeGrammar terminal-yield finite window]
\label{thm:contextfreegrammar-terminal-yield-window}
For an accepted $\ContextFreeGrammarUp$ packet
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
and a displayed finite derivation window selected by a
$\mathsf{ProbeBundle}$, suppose the selected production rows are stable under
the packet's componentwise $\hsame$ rows, the selected derivation segments
concatenate through their displayed sentential-form endpoints, and the final
sentential form has the readback row $y$. Then every selected terminal row is
read through the same $\mathsf{BHist}$ carrier, $\hsame$ transport,
$\Cont$ route, $\Pkg$ provenance, and $\NameCert_{\ContextFreeGrammarUp}$
ledger of $G$. No selected nonterminal production row is exposed as a
terminal yield row.
\end{theorem}
\begin{proof}
Begin with the selected production rows in the finite window. Apply
\autoref{thm:contextfreegrammar-production-stability} to each selected
production step, so the left nonterminal, the right-side $\ListUp$ row, and
the terminal and nonterminal tags remain inside the displayed production
ledger $P$ with the same $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ provenance.

Next assemble the selected route. Apply
\autoref{thm:contextfreegrammar-derivation-concatenation} to the displayed
derivation segments whose endpoints agree by the packet's sentential-form
$\hsame$ rows. The concatenated route is still a finite ledger over $P$, so it
does not introduce a host grammar step or an unlisted production row.

Finally apply \autoref{thm:contextfreegrammar-yield-readback} to the terminal
sentential form and the readback row $y$. The readback projects only terminal
rows through the displayed bundle and identifies them with the $\ListUp$ word
row $w$. Since nonterminal tags are preserved by production stability and the
readback row is terminal-only, no nonterminal production row escapes as a
terminal yield.
\end{proof}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_terminal\_yield\_window}

\begin{theorem}[ContextFreeGrammar NameCert obligation surface]
\label{thm:contextfreegrammar-namecert-obligation-surface}
The local $\NameCert_{\ContextFreeGrammarUp}$ obligation surface consists of
five finite rows:
\begin{enumerate}
\item carrier habitation for the terminal alphabet, nonterminal carrier, start
symbol, finite production ledger, terminal word, derivation ledger, readback
row, transport rows, continuation routes, provenance, and local registration;
\item production stability under componentwise $\hsame$ transport by
\autoref{thm:contextfreegrammar-production-stability};
\item derivation concatenation for finite ledger segments by
\autoref{thm:contextfreegrammar-derivation-concatenation};
\item yield readback from the final terminal sentential form to the displayed
$\ListUp$ word row by \autoref{thm:contextfreegrammar-yield-readback};
\item consumer boundary: $\RegularLanguageUp$ and $\TuringMachineUp$ readers
receive only the displayed grammar packet, finite production and derivation
ledgers, yield row, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ provenance.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_namecert\_obligation\_surface}
\begin{proof}
Carrier habitation is exactly the packet of
\autoref{def:contextfreegrammar-bhist-carrier}. Its coordinates are finite
grammar rows, a finite production ledger, a finite derivation ledger, and a
terminal yield row.

The production and derivation rows are supplied by
\autoref{thm:contextfreegrammar-production-stability} and
\autoref{thm:contextfreegrammar-derivation-concatenation}. Together they keep
every derivation step inside the displayed finite ledger and preserve the
transport and continuation routes.

The readback row is \autoref{thm:contextfreegrammar-yield-readback}. It
identifies the terminal fringe with the displayed $\ListUp$ word and repacks
the same rows as the accepted yield read.

Finally project the provenance row $p$. It names the downstream
$\RegularLanguageUp$ and $\TuringMachineUp$ consumer surfaces without adding a
host language quotient, parse-tree infinitary semantics, pumping theorem, or
recognizer completeness claim.
\end{proof}

\begin{theorem}[ContextFreeGrammar RegularLanguage--TuringMachine bridge boundary]
\label{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}
The public grammar and yield packet of
\autoref{def:contextfreegrammar-bhist-carrier} exports to
$\RegularLanguageUp$ and $\TuringMachineUp$ consumers only the terminal
alphabet, nonterminal carrier, start row, finite production ledger, finite
derivation ledger, $\ListUp$ terminal yield row, $\hsame$ transports,
$\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert$ row.

The exported boundary does not include ambiguity, parsing completeness,
pumping arguments, Chomsky normal form, or recognizer completeness.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_regularlanguage\_turingmachine\_bridge\_boundary}
\begin{proof}
Project the finite grammar packet of
\autoref{def:contextfreegrammar-bhist-carrier}. The terminal alphabet,
nonterminal carrier, start row, production ledger, derivation ledger,
terminal yield row, transport rows, continuation routes, provenance, and
naming row are exactly the displayed carrier coordinates.

Use \autoref{thm:contextfreegrammar-production-stability} to keep every
production witness inside the finite ledger under componentwise transport.
Use \autoref{thm:contextfreegrammar-derivation-concatenation} to compose
consumer derivation windows without introducing an infinitary derivation
object.

Apply \autoref{thm:contextfreegrammar-yield-readback} and
\autoref{thm:contextfreegrammar-terminal-yield-window}. These identify the
consumer-visible yield as the same $\ListUp$ terminal word row read through
the finite derivation ledger and the stored terminal readback surface.

Finally apply
\autoref{thm:contextfreegrammar-namecert-obligation-surface} and repack the
rows named by the consumer boundary. Since the packet has no coordinate for
ambiguity, parsing completeness, pumping arguments, Chomsky normal form, or a
complete recognizer, none of those structures is exported to
$\RegularLanguageUp$ or $\TuringMachineUp$ readers.
\end{proof}

\begin{theorem}[ContextFreeGrammar consumer boundary determinacy]
\label{thm:contextfreegrammar-consumer-boundary-determinacy}
Let $G$ and $H$ be accepted finite $\ContextFreeGrammarUp$ packets. Suppose
their terminal alphabet rows, nonterminal carrier rows, start rows, production
ledgers, derivation ledgers, yield rows, $\hsame$ rows, $\Cont$ rows,
$\mathsf{Pkg}$ provenance rows, and local $\NameCert$ rows agree
componentwise. Then $G$ and $H$ induce the same consumer-visible boundary for
both $\RegularLanguageUp$ and $\TuringMachineUp$ readers.

The common boundary is the finite grammar and yield surface exported by
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}.
It contains no grammar-equivalence quotient, ambiguity row, parsing-completeness
row, pumping argument, Chomsky-normal-form witness, or recognizer-completeness
coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_consumer\_boundary\_determinacy}
\begin{proof}
Apply \autoref{thm:contextfreegrammar-production-stability} to the equal
production ledgers. The production witnesses of $G$ and $H$ stay inside the
same finite terminal and nonterminal rows under the displayed componentwise
$\hsame$ transports.

Next apply \autoref{thm:contextfreegrammar-derivation-concatenation}. The
equal derivation ledgers concatenate through the same sentential-form endpoints
and therefore expose the same finite derivation route to downstream consumers.

Apply \autoref{thm:contextfreegrammar-yield-readback}. Since the terminal yield
rows agree, both packets read back to the same $\ListUp$ terminal word through
the same terminal-only surface.

Finally use
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}.
That boundary is built only from the terminal alphabet, nonterminal carrier,
start row, production ledger, derivation ledger, yield row, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and local $\NameCert$ rows. Componentwise equality of exactly
those rows therefore forces the same $\RegularLanguageUp$ and
$\TuringMachineUp$ consumer-visible boundary, while the excluded grammar and
recognizer structures have no exported coordinate.
\end{proof}

\begin{theorem}[ContextFreeGrammar parse-tree derivation boundary]
\label{thm:contextfreegrammar-parse-tree-derivation-boundary}
Every parse-tree-shaped consumer read of an accepted
$\ContextFreeGrammarUp$ packet factors through the finite production rows,
derivation concatenation rows, terminal yield window, $\ListUp$ word row,
$\TuringMachineUp$ bridge boundary, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
local $\NameCert$ rows of \autoref{def:contextfreegrammar-bhist-carrier}. The
read exports no infinitary parse-tree semantics, host language quotient,
pumping theorem, or grammar-equivalence oracle.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_parse\_tree\_derivation\_boundary}
\begin{proof}
Project the accepted packet through
\autoref{def:contextfreegrammar-bhist-carrier}. A parse-tree-shaped consumer
read can name productions, sentential-form steps, and terminal leaves only
through the displayed finite production ledger, derivation ledger, readback
row, transport rows, continuation routes, provenance, and local naming row.

Apply \autoref{thm:contextfreegrammar-production-stability} to keep each
production read inside the finite production ledger. Apply
\autoref{thm:contextfreegrammar-derivation-concatenation} to assemble the
tree-shaped read as a finite derivation route whose subderivations meet at
displayed sentential-form endpoints.

Next apply \autoref{thm:contextfreegrammar-yield-readback} and
\autoref{thm:contextfreegrammar-terminal-yield-window}. These identify the
consumer-visible leaves with the terminal yield window and the $\ListUp$ word
row, while preserving the same $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ provenance.

Finally apply
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}
and \autoref{thm:contextfreegrammar-consumer-boundary-determinacy}. The
bridge exposes only the displayed grammar and yield surface to
$\TuringMachineUp$ and $\RegularLanguageUp$ readers, and determinacy says
that agreeing finite rows determine the same consumer-visible boundary.

Since no carrier coordinate stores an infinitary parse-tree semantics, host
language quotient, pumping theorem, or grammar-equivalence oracle, none of
those structures is exported by the parse-tree-shaped read.
\end{proof}

\closureat{ContextFreeGrammarUp}{seedStr}
\closureat{ContextFreeGrammarUp}{obligationStr}
\closureat{ContextFreeGrammarUp}{scopedStr}
\closureat{ContextFreeGrammarUp}{publicStr}
\closureat{ContextFreeGrammarUp}{bridgedStr}
\closureat{ContextFreeGrammarUp}{matureStr}

\begin{closurestatus}{\ContextFreeGrammarUp}
  \constructivestory{A context-free grammar packet is generated by finite terminal and nonterminal rows, a start row, finite production rows, a ListUp terminal word row, a finite derivation ledger, a terminal yield readback row, displayed transports, continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:contextfreegrammar-bhist-carrier}, \autoref{thm:contextfreegrammar-production-stability}, \autoref{thm:contextfreegrammar-derivation-concatenation}, \autoref{thm:contextfreegrammar-yield-readback}, \autoref{thm:contextfreegrammar-namecert-obligation-surface}, \autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}, \autoref{thm:contextfreegrammar-consumer-boundary-determinacy}, \autoref{thm:contextfreegrammar-parse-tree-derivation-boundary}, and \autoref{thm:contextfreegrammar-derivation-prefix-carrier} bind the carrier, production and derivation rows, yield readback, grammar obligation surface, paper bridge boundary, consumer boundary determinacy, parse-tree-shaped consumer boundary, and finite derivation-prefix subledger treatment for the displayed grammar packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close grammar equivalence, ambiguity, parsing completeness, pumping arguments, Chomsky normal form, context-free language closure theorems, or machine bridge verification.}
  \upgradepath{Machine bridge verification requires a Lean bridge theorem for the displayed grammar packet and its regular-language and Turing-machine consumer surfaces.}
\end{closurestatus}

\begin{theorem}[ContextFreeGrammar derivation prefix carrier]
\label{thm:contextfreegrammar-derivation-prefix-carrier}
Let
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
be an accepted $\ContextFreeGrammarUp$ packet. Suppose the finite derivation
ledger $d$ is displayed as a split into a prefix ledger $d_{\mathrm{pre}}$ and
a suffix ledger $d_{\mathrm{suf}}$, with $d_{\mathrm{pre}}$ beginning at the
start row $S$ and ending at the split sentential-form row $u$. Then
$d_{\mathrm{pre}}$ repacks as an accepted derivation-segment carrier
$$
(S,P,d_{\mathrm{pre}},u,h_{\mathrm{pre}},c_{\mathrm{pre}},p,n)
$$
over the same start row, production ledger, package provenance, and local
$\NameCert_{\ContextFreeGrammarUp}$ row. The restricted rows
$h_{\mathrm{pre}}$ and $c_{\mathrm{pre}}$ are exactly the componentwise
$\hsame$ transports and $\Cont$ routes of $h$ and $c$ whose derivation entries
lie in the displayed prefix. The repacked segment contains no suffix step, no
terminal-yield readback requirement, and no production row outside $P$.
\end{theorem}
\leanchecked{BEDC.Derived.ContextFreeGrammarUp.ContextFreeGrammarPacket\_derivation\_prefix\_carrier}
\begin{proof}
Project the accepted packet through
\autoref{def:contextfreegrammar-bhist-carrier}. The coordinate $d$ is a finite
derivation ledger beginning at the displayed start row $S$, and each step of
$d$ replaces one displayed nonterminal occurrence by a production row already
listed in the finite production ledger $P$.

The displayed split selects a finite initial subledger
$d_{\mathrm{pre}}$. Since it is an initial segment of $d$, its first
sentential-form row is still $S$, and its last sentential-form row is the
split row $u$. Every step retained in $d_{\mathrm{pre}}$ is therefore a step
of the original ledger, so its production witness is already a row of $P$.
Applying \autoref{thm:contextfreegrammar-production-stability} to these
retained steps keeps the left nonterminal row, right-side $\ListUp$ row,
terminal and nonterminal tags, and production witness inside the same
displayed production ledger.

Restrict the transport coordinate $h$ to the alphabet, nonterminal,
production, sentential-form, and derivation rows that occur in
$d_{\mathrm{pre}}$. This gives $h_{\mathrm{pre}}$. Restrict the continuation
coordinate $c$ to the route entries that read those same prefix steps. This
gives $c_{\mathrm{pre}}$. Both restrictions are finite because the selected
prefix is a finite subledger of the finite ledger $d$.

Now repack the rows
$S$, $P$, $d_{\mathrm{pre}}$, $u$, $h_{\mathrm{pre}}$,
$c_{\mathrm{pre}}$, $p$, and $n$. They provide exactly the data needed for a
finite derivation segment: a start row, the production ledger used at each
step, the retained derivation rows, the endpoint row, the corresponding
transports, the corresponding continuation routes, package provenance, and
the local naming row. The yield row $w$ and readback row $y$ are not used,
because the claim stops at the split sentential form and does not assert that
$u$ is terminal.

Finally, \autoref{thm:contextfreegrammar-derivation-concatenation} checks the
boundary: concatenating the repacked prefix with the displayed suffix along
the split sentential-form row recovers a finite derivation ledger over the
same production rows. Thus the prefix repacking is a genuine subledger carrier
of the accepted packet, not a separate grammar, parse tree, host closure, or
recognizer-completeness assertion.
\end{proof}

\begin{lemma}[ContextFreeGrammar BHist forgetful projection boundary]
\label{lem:contextfreegrammar-bhist-forgetful-projection-boundary}
Let
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
be an accepted $\ContextFreeGrammarUp$ packet, and put
$$
\partial_{\BHist}(G)=((\Sigma,N,S,w),(P,d,y),h,c,p,n).
$$
Every $\BHist$-level read of $G$ visible to $\RegularLanguageUp$ or
$\TuringMachineUp$ consumers factors through $\partial_{\BHist}(G)$. The
projection retains the target carrier rows $\Sigma,N,S,w$, the production and
derivation ledger rows $P,d,y$, the classifier transports $h$, the
continuation routes $c$, the provenance row $p$, and the local
$\NameCert_{\ContextFreeGrammarUp}$ row $n$. It forgets only display labels
outside those coordinates. In particular, the projection carries no ambiguity
row, grammar-equivalence quotient, parse-tree semantics, pumping datum,
Chomsky-normal-form witness, or recognizer-completeness coordinate.
\end{lemma}
\begin{proof}
Project the accepted packet through
\autoref{def:contextfreegrammar-bhist-carrier}. The carrier definition lists
exactly the finite grammar rows $\Sigma,N,S$, the production ledger $P$, the
terminal word row $w$, the derivation ledger $d$, the readback row $y$, the
transport row $h$, the continuation row $c$, the provenance row $p$, and the
local naming row $n$. The displayed projection $\partial_{\BHist}(G)$ keeps
all rows that a $\BHist$ consumer can inspect after dropping the richer
presentation labels.

For production reads, apply
\autoref{thm:contextfreegrammar-production-stability}. A production witness is
already a row of $P$, and its transported left nonterminal, right-side
$\ListUp$ word, terminal tags, and nonterminal tags are read only through the
componentwise transports in $h$ and the route entries in $c$. Thus forgetting
the surrounding presentation name does not remove any production coordinate
available to the consumer.

For derivation and yield reads, apply
\autoref{thm:contextfreegrammar-derivation-concatenation},
\autoref{thm:contextfreegrammar-yield-readback}, and
\autoref{thm:contextfreegrammar-terminal-yield-window}. These results force a
consumer derivation to pass through the finite ledger $d$, the same production
ledger $P$, the terminal readback row $y$, and the $\ListUp$ terminal word row
$w$, while preserving the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ rows. All of these rows are coordinates of
$\partial_{\BHist}(G)$.

The adjacent consumer chapters
\autoref{ch:concrete-instances-regularlanguage-namecert} and
\autoref{ch:concrete-instances-turingmachine-namecert} receive the grammar
packet only through the consumer boundary described in
\autoref{thm:contextfreegrammar-namecert-obligation-surface} and
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}.
That boundary exports precisely the displayed grammar and yield rows,
transport rows, continuation routes, provenance, and local naming row retained
by $\partial_{\BHist}(G)$.

Finally, \autoref{thm:contextfreegrammar-consumer-boundary-determinacy} says
that componentwise agreement on those retained rows forces the same
$\RegularLanguageUp$ and $\TuringMachineUp$ consumer-visible boundary. Hence
any row not present in $\partial_{\BHist}(G)$ cannot change a visible consumer
read. Since the carrier has no coordinate for ambiguity, grammar equivalence,
infinitary parse-tree semantics, pumping arguments, Chomsky normal form, or
recognizer completeness, the forgetful projection cannot export any of those
structures.
\end{proof}

\begin{lemma}[ContextFreeGrammar BHist classifier alignment boundary]
\label{lem:contextfreegrammar-bhist-classifier-alignment-boundary}
Let
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
and
$$
G'=(\Sigma',N',S',P',w',d',y',h',c',p',n')
$$
be accepted $\ContextFreeGrammarUp$ packets. Suppose the local packet
classifier compares them through the displayed componentwise $\hsame$ rows on
terminal alphabets, nonterminal carriers, start rows, production ledgers,
terminal word rows, derivation ledgers, readback rows, continuation routes,
package provenance, and local naming rows. Then every $\BHist$ classifier read
of $G$ handed to a $\RegularLanguageUp$ or $\TuringMachineUp$ consumer
transports exactly the following displayed rows:
\begin{enumerate}
\item the grammar carrier rows $\Sigma,N,S$ and their counterparts
$\Sigma',N',S'$;
\item each production row of $P$ to the corresponding production row of $P'$,
with transported left nonterminal, terminal and nonterminal tags, and
$\ListUp$ right side;
\item each retained derivation row of $d$ to the corresponding derivation row
of $d'$, with the same sentential-form endpoint comparison;
\item the terminal yield row $w$, the readback row $y$, the transport rows
$h$, continuation routes $c$, package provenance $p$, and local
$\NameCert_{\ContextFreeGrammarUp}$ row $n$, together with their counterparts.
\end{enumerate}
The same read forgets every row outside this list. In particular, it does not
supply a $\RegularLanguageUp$ state carrier, accepting-state carrier,
transition table, deterministic run ledger, accepted endpoint, or a
$\TuringMachineUp$ configuration trace, deterministic transition table,
halted-repetition row, tape readback row, or bounded simulation row unless
that row is separately displayed by the receiving consumer's own carrier.
Thus the receiving classifier gate must re-read the grammar rows through
\autoref{def:contextfreegrammar-bhist-carrier}; it cannot treat a copied
source excerpt as an additional transported coordinate.
\end{lemma}
\begin{proof}
Project both accepted packets through
\autoref{def:contextfreegrammar-bhist-carrier}. The carrier definition lists
only the finite terminal alphabet, nonterminal carrier, start row, production
ledger, terminal word, derivation ledger, readback row, transport row,
continuation row, provenance row, and local naming row. Hence a local
classifier comparison between $G$ and $G'$ has no coordinate other than those
listed rows.

For production rows, apply
\autoref{thm:contextfreegrammar-production-stability}. A production witness is
a visible entry of $P$, and transport carries it to one visible entry of $P'$
with the transported left nonterminal and transported $\ListUp$ right side.
The same theorem preserves terminal and nonterminal tags and rules out any
host production relation. Therefore the production part of the classifier
alignment is exactly the rowwise movement from $P$ to $P'$.

For derivation rows, apply
\autoref{thm:contextfreegrammar-derivation-concatenation} to the displayed
sentential-form endpoints and production witnesses. Every transported
derivation step remains a finite ledger entry over the same transported
production surface. Then apply
\autoref{thm:contextfreegrammar-yield-readback} and
\autoref{thm:contextfreegrammar-terminal-yield-window}. These force the
consumer-visible terminal fringe to be the displayed $\ListUp$ word row $w$
and its transported counterpart $w'$, read through $y,y'$ and the same
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Now compare the receiving consumers. The $\RegularLanguageUp$ accepted-word
classifier of \autoref{def:regularlanguage-classifier} is a classifier on a
displayed finite-automaton packet: alphabet, state, transition, input-word,
run, and accepting-endpoint rows. The grammar packet contributes only the
terminal-yield word and the provenance route named by
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary};
it does not contain the finite-automaton state, transition, run, or endpoint
coordinates. Thus those rows cannot be transported from $G$ by the grammar
classifier.

Similarly,
\autoref{thm:turingmachine-source-classifier-obligation} reads the
$\TuringMachineUp$ source classifier from finite state and tape alphabets,
unary time and head-position rows, a $\SeqUp$ configuration trace,
deterministic transition data, and bounded $\ComputableUp$ trace rows. The
context-free grammar carrier contains none of those machine-source
coordinates. Its bridge contribution is only the displayed grammar and yield
surface identified by
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary}.

Finally apply
\autoref{thm:contextfreegrammar-consumer-boundary-determinacy}. Componentwise
agreement on the retained grammar, production, derivation, yield, transport,
continuation, provenance, and local naming rows determines the same
$\RegularLanguageUp$ and $\TuringMachineUp$ consumer-visible boundary. Since
all other candidate rows are absent from
\autoref{def:contextfreegrammar-bhist-carrier}, they are forgotten by the
$\BHist$ classifier projection and cannot be recovered by quoting the source
presentation rather than re-reading the displayed carrier rows.
\end{proof}

\begin{theorem}[ContextFreeGrammar displayed implication completion boundary]
\label{thm:contextfreegrammar-displayed-implication-completion-boundary}
Let
$$
G=(\Sigma,N,S,P,w,d,y,h,c,p,n)
$$
be an accepted $\ContextFreeGrammarUp$ packet. Every displayed forward
classifier or readback implication named in the local grammar chapter is
completed in exactly one of the following two ways.
\begin{enumerate}
\item Production transport is two-sided on the visible production rows. A
production row transported from one accepted packet to a classified mate is read
back as the same finite ledger position with transported left nonterminal,
transported $\ListUp$ right side, and the same terminal and nonterminal tag
rows.
\item Derivation concatenation is two-sided only at a displayed split row. Two
finite derivation segments concatenate through an $\hsame$ endpoint row, and a
ledger with a displayed prefix--suffix split repacks its prefix as the carrier
of \autoref{thm:contextfreegrammar-derivation-prefix-carrier}; no arbitrary
factorization is inferred without such a split row.
\item Yield readback is two-sided on the visible rows $S$, $P$, $d$, $y$, and
$w$. An accepted yield read factors through those rows, and a finite derivation
ledger ending in a terminal sentential form with readback row $y$ repacks as the
same accepted yield read.
\item Terminal-window, consumer-boundary, parse-tree-shaped, and forgetful
$\BHist$ projection reads are one-way interpretation boundaries. They factor a
consumer read through the displayed finite carrier, transport, continuation,
provenance, and naming rows, but they do not reconstruct grammar equivalence,
ambiguity, parsing completeness, pumping data, Chomsky normal form,
infinitary parse-tree semantics, or recognizer completeness.
\end{enumerate}
Thus the chapter has no unrecorded reverse implication: each named forward
surface either has its reverse on the same visible rows or is explicitly bounded
as a one-way interpretation of the displayed $\BHist$ packet.
\end{theorem}
\begin{proof}
Project $G$ through \autoref{def:contextfreegrammar-bhist-carrier}. The only
available coordinates are the terminal alphabet row $\Sigma$, nonterminal
carrier row $N$, start row $S$, finite production ledger $P$, terminal word row
$w$, derivation ledger $d$, readback row $y$, transport row $h$, continuation
row $c$, provenance row $p$, and local naming row $n$.

For production rows, use
\autoref{thm:contextfreegrammar-production-stability}. Its forward direction
transports a displayed production row along the componentwise $\hsame$ rows in
$h$. Its readback direction is the same finite ledger projection in the target
packet. Since the carrier has no coordinate for a host production relation, the
reverse can only return to the visible production row with the transported left
nonterminal, transported $\ListUp$ right side, and preserved terminal and
nonterminal tags.

For derivation rows, use
\autoref{thm:contextfreegrammar-derivation-concatenation} together with
\autoref{thm:contextfreegrammar-derivation-prefix-carrier}. Concatenation gives
the forward implication from two displayed segments and an $\hsame$ endpoint
row to a finite derivation ledger over $P$. The reverse implication is available
exactly when the ledger already displays a prefix--suffix split: the prefix
repackages over the same start row, production ledger, restricted transports,
restricted continuation routes, provenance, and local $\NameCert$ row. Without
a displayed split row, there is no carrier coordinate naming an arbitrary
factorization, so the reverse stops at this boundary.

For yield rows, apply \autoref{thm:contextfreegrammar-yield-readback}. The
forward implication factors an accepted terminal-yield read through the start
row, finite production ledger, finite derivation ledger, terminal readback row,
and $\ListUp$ word row. The converse in the same theorem starts from exactly
those displayed rows and repacks them as the accepted yield read of the same
packet. This is a genuine two-sided completion because both directions use the
same visible rows $S$, $P$, $d$, $y$, and $w$.

For selected terminal windows, use
\autoref{thm:contextfreegrammar-terminal-yield-window}. It sends a displayed
finite derivation window to terminal rows read through the same $\BHist$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance. The theorem also records
the obstruction to reversal: a selected terminal row exposes no selected
nonterminal production row as a terminal yield row. Thus terminal-window reading
is a one-way interpretation unless the carrier already supplies the production
and derivation window.

For downstream consumers, use
\autoref{thm:contextfreegrammar-namecert-obligation-surface},
\autoref{thm:contextfreegrammar-regularlanguage-turingmachine-bridge-boundary},
\autoref{thm:contextfreegrammar-consumer-boundary-determinacy},
\autoref{thm:contextfreegrammar-parse-tree-derivation-boundary}, and
\autoref{lem:contextfreegrammar-bhist-forgetful-projection-boundary}. These
results all project the same displayed grammar and yield surface to
$\RegularLanguageUp$ and $\TuringMachineUp$ readers. Determinacy says that
componentwise agreement on the exported rows forces the same consumer-visible
boundary, but none of those rows is a host language quotient, grammar
comparison oracle, parse-tree semantics, pumping datum, Chomsky-normal-form
witness, ambiguity classifier, or complete recognizer.

The displayed implications have therefore been exhausted by the carrier rows.
Production transport and yield readback have reverses on the same visible rows;
derivation concatenation has a reverse only at displayed split rows; and the
terminal-window, consumer-boundary, parse-tree-shaped, and forgetful $\BHist$
reads are recorded as one-way interpretation boundaries. No further reverse
implication can be formed inside the chapter without adding a coordinate absent
from \autoref{def:contextfreegrammar-bhist-carrier}.
\end{proof}
