\chapter{A Concrete Naming Certificate for $\ContinuedFractionConvergentsUp$}
\label{ch:concrete-instances-continued-fraction-convergents-namecert}
\origin{human}

Following Perron, Khinchin, and the Hardy--Wright treatment of continued
fractions, the $\ContinuedFractionConvergentsUp$ packet names finite
convergent data before any completion-facing consumer reads it as a regular
rational sequence or as a real-name seal. It refines the partial-quotient
surface of \autoref{ch:concrete-instances-continuedfraction-namecert} by
separating the convergent numerator and denominator rows, the rational
normalization rows of \autoref{ch:concrete-instances-rat-namecert}, the
finite-window route of \autoref{ch:concrete-instances-streamname-namecert},
the regular-rational handoff of
\autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal
$\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert}. The
packet is a finite approximation certificate between continued fractions and
Real or Completion routes; it is not a completeness theorem and not a
quotient equality principle.

\begin{definition}[ContinuedFractionConvergents carrier]
\label{def:continued-fraction-convergent-carrier}
A $\ContinuedFractionConvergentsUp$ carrier is a finite $\BHist$ packet
$$
K=(A,N,D,Q,W,E,R,S,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the $\ContinuedFractionUp$ partial-quotient source row, including
the finite prefix of partial quotients and the local recurrence ledger that
names which prefix is being read.
\item $N$ and $D$ are the $\RatUp$ numerator and denominator convergent rows.
They display the finite recurrence steps and the denominator-nonzero side
condition needed to read each convergent as a rational endpoint.
\item $Q$ is the $\RatUp$ normalized rational-convergent row obtained from
$N$ and $D$ by the displayed rational arithmetic route.
\item $W$ is the $\StreamNameUp$ finite-window row exposing only the
convergent indices requested by the downstream consumer.
\item $E$ is the $\DyadicRatCoreUp$ error-ledger row. It records the dyadic
radius, endpoint enclosure, and precision budget attached to each displayed
finite window.
\item $R$ is the $\RegSeqRatUp$ handoff row built from $Q,W,E$ and the
recurrence ledger of $A,N,D$.
\item $S$ is the terminal $\RealUp$ seal reached only after the regular
rational row $R$ has been displayed.
\item $H$ records componentwise $\hsame$ transport for partial quotients,
numerator rows, denominator rows, normalized rationals, stream windows,
dyadic ledgers, regular handoff, the Real seal, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from each finite window request
through $A,N,D,Q,W,E,R,S,H,P,L$.
\item $P$ is the $\Pkg$ provenance row over
$\ContinuedFractionConvergentsUp$, $\ContinuedFractionUp$, $\RatUp$,
$\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$,
$\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\ContinuedFractionConvergentsUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no
coordinate for an infinite continued-fraction tail, host rational equality,
quotient real equality, a selected limit, countable choice, or ambient
$\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.ContinuedFractionConvergentsUp.ContinuedFractionConvergentsTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ContinuedFractionConvergents NameCert obligations]
\label{thm:continued-fraction-convergent-namecert-obligations}
For every accepted $\ContinuedFractionConvergentsUp$ carrier
$K=(A,N,D,Q,W,E,R,S,H,C,P,L)$, the local
$\NameCert_{\ContinuedFractionConvergentsUp}$ surface consists exactly of the
following six obligation rows:
\begin{enumerate}
\item carrier admission for the displayed partial-quotient source, rational
numerator and denominator rows, normalized rational convergent row, finite
stream windows, dyadic error ledger, regular handoff, Real seal, and
structural rows $H,C,P,L$;
\item recurrence exactness, requiring each displayed numerator and denominator
row to read the finite recurrence ledger of $A$ before the rational row $Q$
is available;
\item rational-window compatibility, requiring $Q$ and $W$ to expose the same
finite convergent indices and no unrequested tail data;
\item dyadic error compatibility, requiring $E$ to be attached to the same
finite windows as $W$ and to supply the precision budget consumed by $R$;
\item Real-route nonescape, requiring $S$ to remain terminal with respect to
$A,N,D,Q,W,E,R$ and to expose no detached real object;
\item componentwise transport, replay, provenance, and naming, requiring
$H,C,P,L$ to preserve only the displayed route under $\hsame$ transport and
$\Cont$ replay.
\end{enumerate}
No local obligation is stored outside these six rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from
\autoref{def:continued-fraction-convergent-carrier}. The visible packet
contains the partial-quotient source, the rational numerator and denominator
rows, the normalized rational convergent row, finite windows, dyadic error
data, regular handoff, Real seal, and the structural rows $H,C,P,L$.

Recurrence exactness reads the source row $A$ before $N$ and $D$ are accepted.
The rational row $Q$ is therefore downstream of the finite recurrence ledger,
not a detached rational sequence.

Window and dyadic compatibility read $W$ and $E$ over the same finite index
set. The stream row exposes only requested convergent windows, and the dyadic
row supplies the precision budget that the regular handoff row $R$ consumes.

The Real-route clause follows from the placement of $S$ after $R$. Since the
carrier has no separate coordinate for completed tails, quotient equality, or
selected limits, $H,C,P,L$ can transport and name only the displayed finite
route.
\end{proof}

\begin{theorem}[ContinuedFractionConvergents RegSeqRat handoff]
\label{thm:continued-fraction-convergent-regseqrat-handoff}
Let $K=(A,N,D,Q,W,E,R,S,H,C,P,L)$ be an accepted
$\ContinuedFractionConvergentsUp$ carrier. Every $\RegSeqRatUp$ consumer reads
the packet through the displayed route
$$
A,N,D \longmapsto Q \longmapsto W,E \longmapsto R \longmapsto H,C,P,L .
$$
Consequently the consumer receives finite continued-fraction prefixes,
rational numerator and denominator rows, normalized rational convergents,
finite stream windows, dyadic error ledgers, componentwise $\hsame$ transport,
$\Cont$ replay, package provenance, and the local NameCert row before any
regular-rational data is available. The route cannot use quotient real
equality, a choice-selected limit, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a $\RegSeqRatUp$ read of $K$. By
\autoref{def:continued-fraction-convergent-carrier}, the only regular
rational coordinate is $R$, and it is downstream of $Q,W,E$ together with the
recurrence ledger carried by $A,N,D$.

The rational part of the route is fixed by $N,D,Q$. The numerator and
denominator rows expose the finite recurrence data, while $Q$ records the
normalized rational convergent surface read through
\autoref{ch:concrete-instances-rat-namecert}.

The window and precision part of the route is fixed by $W$ and $E$. The
finite stream surface of
\autoref{ch:concrete-instances-streamname-namecert} chooses the displayed
windows, and the $\DyadicRatCoreUp$ ledger supplies the error budget consumed
by the regular-rational row of
\autoref{ch:concrete-instances-regseqrat-namecert}.

Finally, $H,C,P,L$ transport, replay, package, and name the same route. Since
the excluded objects have no coordinate in the carrier, every handoff to
$\RegSeqRatUp$ factors through the displayed finite convergent packet.
\end{proof}

\begin{theorem}[ContinuedFractionConvergents Real seal boundary]
\label{thm:continued-fraction-convergent-real-seal-boundary}
Every $\RealUp$ read of an accepted $\ContinuedFractionConvergentsUp$ carrier
factors through the $\RegSeqRatUp$ handoff row $R$ before it reaches the Real
seal row $S$. The boundary exposes the same finite partial-quotient source,
rational convergent rows, finite windows, dyadic error ledger, transport,
replay, provenance, and local naming; it does not assert full real
completeness, quotient equality of real names, or a choice-selected limit of
the convergent sequence.
\end{theorem}
\begin{proof}
Read the Real-facing coordinate of
\autoref{def:continued-fraction-convergent-carrier}. The seal row is $S$, and
the definition places $S$ after the regular handoff row $R$.

Apply \autoref{thm:continued-fraction-convergent-regseqrat-handoff}. The
handoff row already factors through the finite partial-quotient source,
rational numerator and denominator rows, normalized rational convergents,
stream windows, dyadic error ledgers, and structural rows.

Thus any Real-facing consumer receives the same finite route before the seal
is visible. No coordinate can bypass $R$ to provide quotient equality,
choice-selected limits, or ambient completeness for $\RealUp$.
\end{proof}

\closureat{ContinuedFractionConvergentsUp}{seedStr}

\begin{closurestatus}{\ContinuedFractionConvergentsUp}
  \constructivestory{A $\ContinuedFractionConvergentsUp$ packet is generated from a ContinuedFraction partial-quotient source, Rat numerator and denominator convergent rows, StreamName finite windows, a DyadicRatCore error ledger, RegSeqRat handoff, Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:continued-fraction-convergent-carrier}, \autoref{thm:continued-fraction-convergent-namecert-obligations}, \autoref{thm:continued-fraction-convergent-regseqrat-handoff}, and \autoref{thm:continued-fraction-convergent-real-seal-boundary} seed the finite continued-fraction convergent route consumed by RegSeqRat and Real packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close full real completeness, quotient equality of real names, choice-selected limits of convergent sequences, total continued-fraction expansion for every real, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, recurrence exactness, rational-window compatibility, dyadic error compatibility, Real-route nonescape, componentwise transport, provenance, and local naming for the same displayed packet.}
\end{closurestatus}
