\chapter{A Concrete Naming Certificate for $\RegularCauchyCompletionUniquenessUp$}
\label{ch:concrete-instances-regular-cauchy-completion-uniqueness-namecert}
\origin{human}

Following Bishop and Bridges' constructive regular Cauchy completion, the $\RegularCauchyCompletionUniquenessUp$ packet isolates the finite uniqueness boundary for comparing two completion handoff routes before any quotient or ambient completeness principle is available. It sits on the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the Bishop completion handoff of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, and the frontier route of \autoref{ch:concrete-instances-regular-cauchy-completion-frontier-namecert}. The packet records only the displayed common-tail comparison by which two accepted regular-Cauchy completion routes expose the same terminal seal boundary.

\begin{definition}[Regular Cauchy completion uniqueness carrier]
\label{def:regular-cauchy-completion-uniqueness-carrier}
A $\RegularCauchyCompletionUniquenessUp$ carrier is a paired finite $\BHist$ packet
$$
U=(L,R,D,S,Q,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the left completion handoff route, read through the $\BishopRegularCauchyCompletionUp$ boundary before any terminal seal is compared.
\item $R$ is the right completion handoff route, read through the $\RegularCauchyCompletionFrontierUp$ boundary with the same consumer-facing precision request.
\item $D$ is the shared $\DyadicRatCoreUp$ tolerance row used by both routes.
\item $S$ is the shared $\StreamNameUp$ finite-window row opened by the tolerance row $D$.
\item $Q$ is the $\RegSeqRatUp$ regular rational readback row exposed inside the same finite window.
\item $E$ is the terminal $\RealUp$ seal row reached by both displayed handoffs after $D,S,Q$ have been fixed.
\item $T$ is the shared-tail comparison row, recording that the two routes are compared only after the common dyadic tolerance, stream window, and regular rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the paired handoff rows, shared tolerance, window, readback, seal, tail comparison, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-facing precision request through $D,S,Q,T$ into the paired handoff rows $L,R$ and the terminal seal row $E$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyCompletionUniquenessUp$, $\BishopRegularCauchyCompletionUp$, $\RegularCauchyCompletionFrontierUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyCompletionUniquenessUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $L,R,D,S,Q,E,T,H,C,P,N$. The carrier has no coordinate for quotient streams, selected limits, countable choice, host real equality, or ambient Real completeness.
\end{definition}

\begin{theorem}[Regular Cauchy completion uniqueness NameCert obligation surface]
\label{thm:regular-cauchy-completion-uniqueness-namecert-obligation-surface}
For every accepted $\RegularCauchyCompletionUniquenessUp$ carrier
$$
U=(L,R,D,S,Q,E,T,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyCompletionUniquenessUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the paired completion handoff routes, shared dyadic tolerance row, stream-window row, regular rational readback row, terminal Real seal row, shared-tail comparison row, transport, replay, provenance, and local naming row;
\item paired-route exposure, requiring both $L$ and $R$ to be displayed before the local classifier compares their completion-facing terminal seal routes;
\item shared-tail comparison, requiring the comparison to pass through the same $D,S,Q$ rows before either handoff route reaches $E$;
\item terminal-seal coincidence, requiring the consumer-visible seal row $E$ to be read only as the common endpoint of the two displayed routes after $T$ has fixed the shared tail surface;
\item classifier transport, requiring componentwise $\hsame$ in $H$ and displayed $\Cont$ replay in $C$ to preserve the ordered route $D,S,Q,T,L,R,E$;
\item ledger non-escape, requiring $P$ and $N$ to export no quotient stream equality, selected limit, countable-choice schedule, host real equality, or ambient Real completeness theorem.
\end{enumerate}
No uniqueness obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyCompletionUniquenessUp.RegularCauchyCompletionUniquenessUpTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:regular-cauchy-completion-uniqueness-carrier}. The displayed tuple supplies exactly the two handoff rows, the shared tolerance-window-readback rows, the terminal seal, the comparison row, and the structural transport, replay, provenance, and naming rows.

Paired-route exposure is forced by the placement of $L$ and $R$. A consumer cannot compare completion handoffs until both routes have been opened as finite $\BHist$ data, one through the Bishop completion boundary and the other through the frontier boundary.

The shared-tail comparison is the row $T$ governed by $D,S,Q$. It fixes the common dyadic tolerance, the same finite StreamName window, and the same regular rational readback before either route is allowed to claim the terminal seal row.

Terminal-seal coincidence is therefore a displayed endpoint fact about $E$, not an equality of quotient streams or host real values. The seal is reached only after the common tail surface has already been read.

Finally, componentwise $\hsame$ in $H$ and displayed $\Cont$ replay in $C$ preserve the ordered route $D,S,Q,T,L,R,E$. Since the carrier contains no quotient, selected-limit, choice, host-equality, or Real-completeness coordinate, the provenance and local NameCert rows cannot export any such object.
\end{proof}

\begin{closurestatus}{\RegularCauchyCompletionUniquenessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-completion-uniqueness-carrier} and \autoref{thm:regular-cauchy-completion-uniqueness-namecert-obligation-surface} seed the finite uniqueness boundary for paired regular-Cauchy completion handoffs through shared dyadic tolerance, stream-window, regular rational readback, terminal Real seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local NameCert rows.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RegularCauchyCompletionUniquenessUp.RegularCauchyCompletionUniquenessUpTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean theorems for carrier admission, paired-route exposure, shared-tail comparison, terminal-seal coincidence, classifier transport, and ledger non-escape for BEDC.Derived.RegularCauchyCompletionUniquenessUp.}
  \constructivestory{A $\RegularCauchyCompletionUniquenessUp$ packet is generated from two completion handoff rows, one shared dyadic tolerance, one finite StreamName window, one RegSeqRat readback, one terminal Real seal, one shared-tail comparison, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
