\chapter{A Concrete Naming Certificate for $\FiniteBracketingIntervalUp$}
\label{ch:concrete-instances-finite-bracketing-interval-namecert}
\origin{human}

Following Bishop and Bridges' constructive interval methods, the $\FiniteBracketingIntervalUp$ packet records the finite BEDC surface at which a real approximation route is bracketed by dyadic endpoints before any $\RealUp$ read is exported. It sits on the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the finite density route of \autoref{ch:concrete-instances-real-separability-namecert}. The packet is a bracketing certificate for displayed endpoint windows; it is not a quotient real interval, selected host limit, trichotomy row, ambient completeness principle, or open-cover compactness argument.

\begin{definition}[Finite bracketing interval carrier]
\label{def:finite-bracketing-interval-carrier}
A $\FiniteBracketingIntervalUp$ carrier is a finite $\BHist$ packet
$$
I=(L,U,D,W,R,E,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ and $U$ are the lower and upper endpoint rows, both named inside the $\DyadicRatCoreUp$ ledger.
\item $D$ is the dyadic-radius containment row, recording the requested tolerance and the finite comparison budget for $L \leq U$.
\item $W$ is the $\StreamNameUp$ observation window inspected under the same tolerance request.
\item $R$ is the $\RegSeqRatUp$ finite-window handoff row that reads $W$ as regular rational data between the endpoint rows.
\item $E$ is the terminal $\RealUp$ seal row available only after $L,U,D,W,R$ have been displayed.
\item $S$ is the $\RealSeparabilityUp$ density-support row, recording that a finite rational candidate can be inspected inside the same bracket when a density consumer requests one.
\item $H$ stores componentwise $\hsame$ transport for endpoint, radius, window, readback, seal, density-support, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a bracketing request through $L,U,D,W,R,E,S$.
\item $P$ is the $\Pkg$ provenance over $\FiniteBracketingIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RealSeparabilityUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteBracketingIntervalUp}$ row.
\end{enumerate}
The carrier has no coordinate for host real equality, quotient stream equality, selected limits, countable choice, ambient completeness, trichotomy, open-cover compactness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.FiniteBracketingIntervalUp.FiniteBracketingIntervalTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite bracketing endpoint order]
\label{thm:finite-bracketing-interval-endpoint-order}
For every accepted $\FiniteBracketingIntervalUp$ carrier
$$
I=(L,U,D,W,R,E,S,H,C,P,N),
$$
the endpoint order read is exhausted by the displayed $\DyadicRatCoreUp$ rows $L,U,D$. A consumer may read the bracket only after the same finite comparison budget has recorded $L \leq U$, and no host order on $\RealUp$, trichotomy row, quotient stream equality, selected midpoint, or ambient completeness datum can replace that dyadic endpoint ledger.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-bracketing-interval-carrier}. The only endpoint rows are $L$ and $U$, and the only comparison budget attached to them is $D$.

Read these rows through the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The comparison is therefore a finite ledger entry over named dyadic endpoints, not an external order assertion about host reals.

The remaining rows $W,R,E,S,H,C,P,N$ preserve, replay, source, and name the same endpoint packet. Since none of them contains host real equality, quotient stream equality, selected midpoint data, trichotomy, or ambient completeness, the endpoint order is exhausted by $L,U,D$.
\end{proof}

\begin{theorem}[Finite bracketing dyadic-radius containment]
\label{thm:finite-bracketing-interval-dyadic-radius-containment}
Every accepted $\FiniteBracketingIntervalUp$ containment read is witnessed by the same finite dyadic-radius row $D$ together with the endpoint rows $L,U$ and the opened $\StreamNameUp$ window $W$. The read states that the inspected window is contained in the displayed bracket at the requested dyadic radius before the $\RegSeqRatUp$ handoff or $\RealUp$ seal is available.
\end{theorem}
\begin{proof}
Begin with an accepted containment read. By \autoref{def:finite-bracketing-interval-carrier}, the tolerance request has only one dyadic-radius row $D$, and it is tied to the endpoint rows $L,U$.

The finite window stage is then $W$. The StreamName surface of \autoref{ch:concrete-instances-streamname-namecert} supplies exactly the inspected observations at the requested radius, so containment is checked before regular rational readback.

Only after $L,U,D,W$ are displayed may the route pass to $R$ and then $E$. Thus the containment read cannot be supplied by a quotient stream, selected host limit, countable choice, ambient completeness, or a detached $\RealUp$ equality.
\end{proof}

\begin{theorem}[Finite bracketing RegSeqRat handoff]
\label{thm:finite-bracketing-interval-regseqrat-handoff}
Every finite-window consumer of an accepted $\FiniteBracketingIntervalUp$ packet factors through the route
$$
\DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp .
$$
Concretely, the consumer first reads $L,U,D$, then the finite window $W$, then the regular rational handoff $R$, and only then the terminal seal $E$.
\end{theorem}
\begin{proof}
Project the carrier. The dyadic endpoint and radius rows $L,U,D$ precede the finite observation row $W$, and $W$ precedes the readback row $R$.

Use the RegSeqRat chapter \autoref{ch:concrete-instances-regseqrat-namecert}. Its public handoff reads finite StreamName windows as regular rational data before any Real-facing seal can consume them.

The terminal row is $E$, the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The route has no coordinate for quotient stream equality, selected limits, countable choice, or $\RealUp$ completeness, so the displayed handoff is the whole public consumer surface.
\end{proof}

\begin{theorem}[Finite bracketing RealUp seal non-escape]
\label{thm:finite-bracketing-interval-real-seal-nonescape}
An accepted $\FiniteBracketingIntervalUp$ packet exports a $\RealUp$ read only through the terminal seal row $E$ after the endpoint order, dyadic-radius containment, finite-window read, RegSeqRat handoff, and RealSeparability density-support rows have already been displayed. No consumer can escape from the bracket into host real equality, selected limits, quotient streams, countable choice, ambient completeness, open-cover compactness, or a detached dense subset.
\end{theorem}
\begin{proof}
Apply the preceding endpoint, containment, and handoff theorems. They force a Real-facing read to pass through $L,U,D,W,R$ before $E$ is available.

The density-support row $S$ is read through \autoref{ch:concrete-instances-real-separability-namecert}. It supplies only the finite rational-window support for a density request inside the same bracket, not an externally chosen dense point.

Finally inspect the structural rows $H,C,P,N$. They transport, replay, source, and name the displayed packet, and the carrier contains no coordinate for host real equality, selected limits, quotient streams, countable choice, ambient completeness, open-cover compactness, or detached dense subsets. Therefore the terminal seal row is a non-escape boundary.
\end{proof}

\begin{theorem}[Finite bracketing interval sibling route]
\label{thm:finite-bracketing-interval-sibling-route}
Every bracket accepted by the $\FiniteBracketingIntervalUp$ carrier reads the located interval endpoint surface, dyadic endpoint ledger, $\StreamNameUp$ window, $\RegSeqRatUp$ handoff, $\RealUp$ seal, and $\RealSeparabilityUp$ density-support row in that order. The route consumes \autoref{ch:concrete-instances-located-real-interval-namecert} for the endpoint surface and \autoref{ch:concrete-instances-real-separability-namecert} for the finite density support before the local structural rows $H,C,P,N$ package the bracket.
\end{theorem}
\begin{proof}
Project the carrier. The endpoint rows $L,U$ and dyadic-radius ledger $D$ provide the finite endpoint surface, and the local introduction ties that surface to the located real interval route.

Use the finite-window RegSeqRat handoff theorem. It forces the consumer through the $\StreamNameUp$ window $W$ and $\RegSeqRatUp$ readback $R$ before the terminal $\RealUp$ seal $E$ can be read.

Use the RealUp seal non-escape theorem. It requires the density-support row $S$ to remain the $\RealSeparabilityUp$ row cited from \autoref{ch:concrete-instances-real-separability-namecert}, not a detached dense subset or chosen point.

Therefore the sibling route is exactly the located endpoint surface, dyadic endpoint ledger, finite window, regular rational handoff, real seal, and separability support, followed only by transport, replay, provenance, and local naming.
\end{proof}

\closureat{FiniteBracketingIntervalUp}{seedStr}

\begin{closurestatus}{\FiniteBracketingIntervalUp}
  \constructivestory{A $\FiniteBracketingIntervalUp$ packet is generated from lower and upper DyadicRatCore endpoint rows, a dyadic-radius containment ledger, a StreamName finite observation window, a RegSeqRat handoff row, a RealUp terminal seal, a RealSeparability density-support row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-bracketing-interval-carrier}, \autoref{thm:finite-bracketing-interval-endpoint-order}, \autoref{thm:finite-bracketing-interval-dyadic-radius-containment}, \autoref{thm:finite-bracketing-interval-regseqrat-handoff}, and \autoref{thm:finite-bracketing-interval-real-seal-nonescape} seed the finite bracketing route over dyadic endpoints, StreamName windows, RegSeqRat readback, RealUp seal, and RealSeparability density support.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real equality, quotient stream equality, selected limits, countable choice, ambient completeness, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked endpoint order, dyadic-radius containment, finite-window RegSeqRat handoff, and RealUp seal non-escape for BEDC.Derived.FiniteBracketingIntervalUp.}
\end{closurestatus}
