\chapter{A Concrete Naming Certificate for $\LocatedClosedIntervalFiniteNetUp$}
\label{ch:concrete-instances-located-closed-interval-finite-net-namecert}
\origin{human}

Following Bishop and Bridges' constructive interval compactness and finite-net methods, the $\LocatedClosedIntervalFiniteNetUp$ packet names the finite BEDC surface at which a located closed interval admits a displayed mesh row before any completion-facing consumer reads a cover claim. It sits after the located endpoint surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, the bracketing packet of \autoref{ch:concrete-instances-finite-bracketing-interval-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet records a finite net for a displayed located interval; it is not a general Heine-Borel theorem, an open-cover compactness principle, a quotient interval, a selected host limit, or an ambient completeness coordinate.

\begin{definition}[Located closed interval finite-net carrier]
\label{def:located-closed-interval-finite-net-carrier}
A $\LocatedClosedIntervalFiniteNetUp$ carrier is a finite $\BHist$ packet
$$
F=(I,M,N,D,W,R,E,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\LocatedRealIntervalUp$ source row, displaying the lower and upper endpoint names together with the located interval boundary that consumers may inspect.
\item $M$ is the mesh-scale row, a finite dyadic tolerance request read through the same endpoint boundary.
\item $N$ is the finite net row, listing the displayed mesh points admitted between the located endpoints at scale $M$.
\item $D$ is the $\DyadicRatCoreUp$ coverage ledger, recording endpoint comparisons, mesh-step arithmetic, and the finite containment checks for the net row.
\item $W$ is the $\StreamNameUp$ observation-window row opened only for the endpoint and mesh requests already displayed by $I,M,D$.
\item $R$ is the $\RegSeqRatUp$ readback row that interprets the opened windows as regular rational data along the same finite mesh route.
\item $E$ is the terminal $\RealUp$ seal row, available only after the located interval, mesh, net, dyadic ledger, windows, and readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval source, mesh scale, net row, coverage ledger, window row, readback row, seal row, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a finite-net request through $I,M,N,D,W,R,E$.
\item $P$ is the $\Pkg$ provenance over $\LocatedClosedIntervalFiniteNetUp$, $\LocatedRealIntervalUp$, $\FiniteBracketingIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\LocatedClosedIntervalFiniteNetUp}$ row.
\end{enumerate}
The carrier has no coordinate for open-cover compactness, general Heine-Borel compactness, host interval equality, quotient representatives, selected real limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.LocatedClosedIntervalFiniteNetUp.LocatedClosedIntervalFiniteNetTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located closed interval finite-net coverage]
\label{thm:located-closed-interval-finite-net-coverage}
For every accepted $\LocatedClosedIntervalFiniteNetUp$ carrier
$$
F=(I,M,N,D,W,R,E,H,C,P,L),
$$
each point read by the local finite-net consumer is covered only through the displayed route
$$
\LocatedRealIntervalUp \longrightarrow \FiniteBracketingIntervalUp \longrightarrow \DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp .
$$
Concretely, the consumer first reads the located interval source $I$, then the mesh scale $M$, then the finite net row $N$, then the dyadic coverage ledger $D$, and only then opens the finite windows $W$ and readback row $R$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source interval row is $I$, and the only mesh data are the scale $M$, the net row $N$, and the dyadic coverage ledger $D$.

Use \autoref{ch:concrete-instances-located-real-interval-namecert} for the endpoint surface and \autoref{ch:concrete-instances-finite-bracketing-interval-namecert} for the finite bracketing route. The bracket read is therefore a displayed interval-and-endpoint computation before any stream window is opened.

The remaining coverage work is finite. The dyadic ledger $D$ records the mesh-step arithmetic and containment checks, while $W$ and $R$ expose only the StreamName windows and RegSeqRat readback attached to that displayed ledger.

The excluded compactness principles have no coordinate in $F$. Thus the coverage read is a finite-net route over the listed rows, not an open-cover or ambient-completeness argument.
\end{proof}

\begin{theorem}[Located closed interval finite-net Real seal non-escape]
\label{thm:located-closed-interval-finite-net-real-seal-nonescape}
An accepted $\LocatedClosedIntervalFiniteNetUp$ packet exports a $\RealUp$ read only through the terminal seal row $E$ after $I,M,N,D,W,R$ have already been displayed. No consumer can escape from the finite net into general Heine-Borel compactness, open-cover compactness, host interval equality, quotient representatives, selected real limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply the finite-net coverage theorem above. It forces a consumer read through the located source, mesh scale, finite net row, dyadic coverage ledger, finite windows, and regular rational readback before the terminal seal is available.

The seal row $E$ is downstream of that finite route. It records the $\RealUp$ boundary attached to the displayed interval-net computation and does not supply an independent completed-real object.

Finally inspect the structural rows $H,C,P,L$. They transport, replay, source, and name the same finite packet. Since the carrier contains no coordinate for the excluded principles or host objects, the terminal seal is a non-escape boundary.
\end{proof}

\begin{closurestatus}{\LocatedClosedIntervalFiniteNetUp}
  \constructivestory{A $\LocatedClosedIntervalFiniteNetUp$ packet is generated from a located closed interval source, a dyadic mesh scale, a finite net row, a DyadicRatCore coverage ledger, StreamName finite windows, RegSeqRat readback, a RealUp terminal seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-closed-interval-finite-net-carrier}, \autoref{thm:located-closed-interval-finite-net-coverage}, and \autoref{thm:located-closed-interval-finite-net-real-seal-nonescape} seed the finite L10 interval-net route over located endpoints, bracketing rows, dyadic coverage, finite windows, regular rational readback, and the RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close general Heine-Borel compactness, open-cover compactness, host interval equality, quotient representatives, selected real limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net coverage, Real seal non-escape, transport, replay, provenance, and local naming for BEDC.Derived.LocatedClosedIntervalFiniteNetUp.}
\end{closurestatus}
