\chapter{A Concrete Naming Certificate for $\UniformHomeomorphismUp$}
\label{ch:concrete-instances-uniformhomeomorphism-namecert}
\origin{human}

Following Bourbaki and Kelley, the $\UniformHomeomorphismUp$ packet presents a uniform homeomorphism as a bidirectional uniform-continuity certificate between two $\UniformSpaceUp$ rows. It is grounded by the uniform-space surface of \autoref{ch:concrete-instances-uniformspace-namecert}, the modulus discipline of \autoref{ch:concrete-instances-uniformcontinuity-namecert}, the graph and pointwise route of \autoref{ch:concrete-instances-continuousmap-namecert}, the embedding boundary of \autoref{ch:concrete-instances-dense-uniform-embedding-namecert}, and the completion consumer surface of \autoref{ch:concrete-instances-uniformcompletion-namecert}. The chapter records the L10 equivalence route used by completion comparisons without exposing quotient completion equality, selected representatives, host equality, countable choice, or ambient completeness.

\begin{definition}[UniformHomeomorphism carrier]
\label{def:uniform-homeomorphism-carrier}
A $\UniformHomeomorphismUp$ carrier is a finite $\BHist$ packet
$$
U=(X,Y,f,g,F,G,M,N,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the source and target $\UniformSpaceUp$ rows, including only the entourage requests and refinement ledgers visible to the certificate.
\item $f$ and $g$ are the forward and inverse graph rows, read through the $\ContinuousMapUp$ surface and carrying no host function object beyond the displayed graph data.
\item $F$ and $G$ are the forward and inverse uniform-continuity rows, each exposing the source tolerance request, the target tolerance request, and the corresponding finite modulus route.
\item $M$ and $N$ are the forward and inverse modulus rows, respectively, so that each direction has its own displayed tolerance transformer before any completion consumer may read the route.
\item $H$ records inverse-route compatibility: the composites $g\circ f$ and $f\circ g$ are accepted only through displayed graph rows, displayed uniform-continuity rows, and componentwise $\hsame$ transport.
\item $C$ records $\Cont$ replay from a source or target entourage request through the appropriate graph row, the matching modulus row, inverse-route compatibility, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\UniformHomeomorphismUp$, $\UniformSpaceUp$, $\UniformContinuityUp$, $\ContinuousMapUp$, $\DenseUniformEmbeddingUp$, $\UniformCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\UniformHomeomorphismUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,f,g,F,G,M,N,H,C,P,L$. The carrier contains no quotient completion equality, selected representative, host equality of points or maps, countable-choice selector, ambient completeness datum, or hidden completion object.
\end{definition}

\begin{theorem}[UniformHomeomorphism NameCert obligations]
\label{thm:uniform-homeomorphism-namecert-obligations}
For every accepted $\UniformHomeomorphismUp$ carrier $U=(X,Y,f,g,F,G,M,N,H,C,P,L)$, the local $\NameCert_{\UniformHomeomorphismUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source and target $\UniformSpaceUp$ rows, forward and inverse graph rows, forward and inverse uniform-continuity rows, both modulus rows, inverse-route compatibility, replay, provenance, and local naming;
\item classifier bidirectionality, requiring rowwise comparison to preserve both directions at once rather than accepting a one-sided uniform-continuity certificate;
\item stability of both moduli, requiring $M$ and $N$ to transport with their matching graph and uniform-continuity rows under componentwise $\hsame$;
\item inverse-route exactness, requiring the two composites to be read only through $H$ after $f,g,F,G,M,N$ have fixed the displayed bidirectional route;
\item ledger non-escape, requiring $C,P,L$ to replay, source, and name no row from which quotient completion equality, selected representatives, host equality, countable choice, ambient completeness, or a hidden completion object can be exported.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-homeomorphism-carrier}. The packet displays the two uniform-space rows, the two graph rows, the two uniform-continuity rows, both modulus rows, inverse-route compatibility, replay, provenance, and local naming.

Classifier bidirectionality follows because the classifier reads the whole tuple $X,Y,f,g,F,G,M,N,H,C,P,L$. A packet cannot be accepted by comparing only $f,F,M$ or only $g,G,N$; both directions are part of the same displayed row comparison.

Stability of both moduli is the componentwise transport clause. The forward modulus row $M$ travels with $f$ and $F$, while the inverse modulus row $N$ travels with $g$ and $G$, and both transports are recorded in $H$ and replayed through $C$.

Inverse-route exactness is forced after the two directed routes have been fixed. The row $H$ is the only displayed location where the composites $g\circ f$ and $f\circ g$ are named, so a consumer cannot introduce a separate host inverse or quotient-completion equality witness.

Finally, ledger non-escape is exhausted by $C,P,L$. These rows replay, source, and name only the displayed route, and none of them contains selected representatives, host equality, countable choice, ambient completeness, or a hidden completion object.
\end{proof}
\leanchecked{BEDC.Derived.UniformHomeomorphismUp.UniformHomeomorphismTasteGate\_single\_carrier\_alignment}

\begin{theorem}[UniformHomeomorphism bidirectional modulus route]
\label{thm:uniform-homeomorphism-bidirectional-modulus-route}
Every accepted $\UniformHomeomorphismUp$ consumer route factors through both displayed moduli $M$ and $N$ along the finite route
$$
X,Y\longmapsto f,g\longmapsto F,G\longmapsto M,N\longmapsto H\longmapsto C,P,L .
$$
Consequently the packet cannot read quotient completion equality, selected representatives, host equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a consumer route for an accepted packet and project the carrier rows. The source and target uniformities are visible only as $X$ and $Y$, and the directed graphs are visible only as $f$ and $g$.

The route must then read the two uniform-continuity rows $F$ and $G$. The forward read exposes the modulus row $M$, and the inverse read exposes the modulus row $N$; omitting either one would leave only a one-sided continuity route rather than a uniform homeomorphism packet.

After both moduli have been read, the inverse-route row $H$ records the displayed composites. This is the only route by which the consumer sees bidirectionality, so quotient completion equality, selected representatives, and host equality are not available as alternate witnesses.

The structural rows $C,P,L$ close the consumer route by replay, provenance, and local naming. Since these rows name only $X,Y,f,g,F,G,M,N,H$, the packet exports no countable-choice selector, ambient completeness datum, or hidden completion object.
\end{proof}

\begin{closurestatus}{\UniformHomeomorphismUp}
  \constructivestory{A $\UniformHomeomorphismUp$ packet is generated from two UniformSpace rows, forward and inverse graph rows, forward and inverse UniformContinuity rows, two displayed modulus rows, inverse-route compatibility, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-homeomorphism-carrier}, \autoref{thm:uniform-homeomorphism-namecert-obligations}, and \autoref{thm:uniform-homeomorphism-bidirectional-modulus-route} seed the finite bidirectional uniform-equivalence packet for L10 completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, host equality, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier bidirectionality, stability of both moduli, inverse-route exactness, and ledger non-escape proofs for BEDC.Derived.UniformHomeomorphismUp.}
\end{closurestatus}
