\chapter{A Concrete Naming Certificate for $\LocatedCompletionSealUp$}
\label{ch:concrete-instances-located-completion-seal-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedCompletionSealUp$ packet names the finite seal by which located Cauchy source data reaches the terminal Real route without turning that route into an ambient completeness theorem. It sits over the regular Cauchy completion boundary of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, the located regular source of \autoref{ch:concrete-instances-regular-located-cauchy-real-namecert}, the tail envelope of \autoref{ch:concrete-instances-located-real-tail-envelope-namecert}, the regular rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite located-completion boundary for $\RealUp$ consumers; it is not Real completeness, quotient stream equality, a selected limit, countable choice, trichotomy, or host real equality.

\begin{definition}[Located completion seal carrier]
\label{def:located-completion-seal-carrier}
A $\LocatedCompletionSealUp$ carrier is a finite $\BHist$ packet
$$
L=(D,S,R,Q,E,A,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ endpoint and tolerance row, containing the dyadic radii, comparisons, and interval endpoints read by the located completion route.
\item $S$ is the $\StreamNameUp$ finite-window row opened before any regular rational or located-tail read.
\item $R$ is the $\RegSeqRatUp$ source row, recording the regular rational observations available on the windows named by $S$ and measured by $D$.
\item $Q$ is the $\RegularLocatedCauchyRealUp$ source row, binding the regular rational source to the displayed locatedness and modulus data.
\item $E$ is the $\LocatedRealTailEnvelopeUp$ row, recording the finite tail window through which the located source is exposed to completion consumers.
\item $A$ is the $\BishopRegularCauchyCompletionUp$ completion-facing boundary row, consuming the same dyadic, stream, and regular rational data as $D,S,R$.
\item $T$ is the terminal $\RealUp$ seal, exposed only after $D,S,R,Q,E,A$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for dyadic, stream, regular rational, located-source, tail-envelope, completion-boundary, Real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each located-completion precision request through $D,S,R,Q,E,A,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedCompletionSealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RegularLocatedCauchyRealUp$, $\LocatedRealTailEnvelopeUp$, $\BishopRegularCauchyCompletionUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCompletionSealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S,R,Q,E,A,T,H,C,P,N$. The carrier has no coordinate for Real completeness, quotient stream equality, selected limits, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.LocatedCompletionSealUp.LocatedCompletionSealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located completion seal NameCert obligations]
\label{thm:located-completion-seal-namecert-obligations}
For every accepted $\LocatedCompletionSealUp$ carrier
$$
L=(D,S,R,Q,E,A,T,H,C,P,N),
$$
the local $\NameCert_{\LocatedCompletionSealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the dyadic ledger, finite stream windows, regular rational source, regular located Cauchy source, located tail envelope, Bishop regular completion boundary, terminal Real seal, transport, replay, provenance, and local naming row;
\item located-source routing, requiring every completion-facing request to read $D,S,R$ before it may read the regular located source row $Q$;
\item tail-envelope compatibility, requiring $E$ to consume the same dyadic, stream, regular rational, and located-source rows as the request that enters the packet;
\item completion-boundary compatibility, requiring $A$ to expose only the displayed regular Cauchy completion boundary over $D,S,R$ and not a selected point of a completed space;
\item Real handoff, requiring $T$ to be downstream of $D,S,R,Q,E,A$ for every $\RealUp$ consumer named by $P$;
\item ledger non-escape, requiring $H,C,P,N$ to preserve and name exactly this finite route and to export no Real completeness, quotient stream equality, selected limit, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.LocatedCompletionSealUp.LocatedCompletionSealNameCert\_obligation\_rows\_exact}
\begin{proof}
Carrier exposure is projection from \autoref{def:located-completion-seal-carrier}. The displayed packet contains the dyadic row $D$, stream windows $S$, regular rational row $R$, located source row $Q$, located tail envelope $E$, Bishop regular completion boundary $A$, terminal Real seal $T$, and the structural rows $H,C,P,N$.

The located-source route is fixed by the row order. A precision request first opens the dyadic tolerance ledger, then the finite stream windows, then the regular rational observations, and only then the regular located Cauchy source.

The tail envelope and completion boundary are compatible because they read the same preceding rows. The row $E$ packages the finite located tail route over $D,S,R,Q$, while the row $A$ packages the regular Cauchy completion-facing boundary over $D,S,R$.

The Real handoff is terminal. The row $T$ is exposed only after the located source, tail envelope, and completion boundary have all been displayed.

Finally, the rows $H,C,P,N$ transport, replay, source, and name the same finite route. Since none of the excluded objects appears as a coordinate of the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Located completion seal Real handoff]
\label{thm:located-completion-seal-real-handoff}
Let $L=(D,S,R,Q,E,A,T,H,C,P,N)$ be an accepted $\LocatedCompletionSealUp$ carrier. Every $\RealUp$ consumer read factors through the finite route
$$
D \longmapsto S \longmapsto R \longmapsto Q \longmapsto E \longmapsto A \longmapsto T \longmapsto H,C,P,N .
$$
Consequently the consumer receives a dyadic tolerance ledger, finite stream windows, regular rational observations, regular located Cauchy source data, a located tail envelope, a Bishop regular Cauchy completion boundary, a terminal Real seal, transport, replay, provenance, and local naming. The handoff cannot use Real completeness, quotient stream equality, a selected limit, countable choice, trichotomy, or host real equality.
\end{theorem}
\begin{proof}
Project the accepted carrier by \autoref{def:located-completion-seal-carrier}. The only Real-facing endpoint is $T$, and the carrier places $T$ after the dyadic, stream, regular rational, located-source, tail-envelope, and completion-boundary rows.

The analytic route starts with $D,S,R$. These rows fix the tolerance ledger, finite observation windows, and regular rational readback before any located completion claim is visible.

The located completion seal is then read through $Q,E,A$. The row $Q$ binds the source as a regular located Cauchy real, $E$ exposes the finite located tail envelope, and $A$ records the completion-facing boundary without selecting a completed point.

The structural rows preserve the same order. Componentwise $\hsame$ transport and displayed $\Cont$ replay cannot introduce a second route to $T$, and the provenance and local naming rows add no excluded coordinate. Hence every $\RealUp$ read factors through the displayed finite route.
\end{proof}

\closureat{LocatedCompletionSealUp}{seedStr}

\begin{closurestatus}{\LocatedCompletionSealUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-completion-seal-carrier}, \autoref{thm:located-completion-seal-namecert-obligations}, and \autoref{thm:located-completion-seal-real-handoff} seed the finite located-completion seal through which DyadicRatCore, StreamName, RegSeqRat, RegularLocatedCauchyReal, LocatedRealTailEnvelope, BishopRegularCauchyCompletion, and Real rows are read in one displayed route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient stream equality, selected limits, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, located-source routing, tail-envelope compatibility, completion-boundary compatibility, Real handoff, and ledger non-escape for BEDC.Derived.LocatedCompletionSealUp.}
  \constructivestory{A $\LocatedCompletionSealUp$ packet is generated from a DyadicRatCore tolerance ledger, StreamName finite windows, a RegSeqRat source row, a RegularLocatedCauchyReal source row, a LocatedRealTailEnvelope row, a BishopRegularCauchyCompletion boundary row, a terminal RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
