\chapter{A Concrete Naming Certificate for $\RegularCauchySequentialCompletenessUp$}
\label{ch:concrete-instances-regular-cauchy-sequential-completeness-namecert}
\origin{human}

Following Bishop and Bridges constructive regular-Cauchy completion, the $\RegularCauchySequentialCompletenessUp$ packet names the finite sequential-completeness surface that sits between regular rational names and the downstream real-facing limit consumer. It reads the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational sequence row of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. It also records the completion-side compatibility supplied by \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, the real-facing consumer boundary of \autoref{ch:concrete-instances-real-sequential-completeness-namecert}, and the extension-and-uniqueness surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}. The packet is a finite NameCert bridge from regular Cauchy sequence data to a displayed limit seal; it is not a quotient stream construction, a selected host limit, countable choice, open-cover compactness, or an ambient $\RealUp$ completeness principle.

\begin{definition}[RegularCauchySequentialCompleteness carrier]
\label{def:regular-cauchy-sequential-completeness-carrier}
A $\RegularCauchySequentialCompletenessUp$ carrier is a finite $\BHist$ packet
$$
Q=(D,S,R,M,L,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, containing the dyadic endpoints and comparison budgets used to inspect the regular Cauchy sequence.
\item $S$ is the $\StreamNameUp$ finite-window row, exposing only the inspected stream windows needed by the sequential-completeness request.
\item $R$ is the $\RegSeqRatUp$ regular rational sequence row read from the windows in $S$ and the tolerance ledger in $D$.
\item $M$ is the regular Cauchy modulus row, assigning each displayed dyadic tolerance a finite tail threshold for the sequence row $R$.
\item $L$ is the displayed $\RealUp$ limit seal reached from $R$ through the same $D,S,M$ route.
\item $U$ is the completion-universal compatibility row, read through $\CompletionUniversalPropertyUp$ after the Bishop regular-Cauchy completion surface has supplied the source and limit routes.
\item $H$ records componentwise $\hsame$ transport for the dyadic ledger, stream windows, regular sequence row, modulus row, limit seal, universal-property row, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a sequential-completeness request through $M,D,S,R,L,U$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchySequentialCompletenessUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRegularCauchyCompletionUp$, $\RealSequentialCompletenessUp$, $\CompletionUniversalPropertyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchySequentialCompletenessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S,R,M,L,U,H,C,P,N$. The carrier has no coordinate for quotient stream equality, selected host limits, countable choice, open-cover compactness, host real equality, or ambient completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchySequentialCompletenessUp.RegularCauchySequentialCompletenessUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RegularCauchySequentialCompleteness NameCert obligations]
\label{thm:regular-cauchy-sequential-completeness-namecert-obligations}
For every accepted $\RegularCauchySequentialCompletenessUp$ carrier $Q=(D,S,R,M,L,U,H,C,P,N)$, the local $\NameCert_{\RegularCauchySequentialCompletenessUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed dyadic tolerance ledger, stream-window row, regular rational sequence row, regular Cauchy modulus, limit seal, completion-universal compatibility row, transport, replay, provenance, and local naming row;
\item classifier stability, requiring componentwise $\hsame$ transport in $H$ to preserve the rows $D,S,R,M,L,U$ before the local classifier identifies two accepted packets;
\item regular-sequence tail control, requiring each tolerance request to read its finite threshold from $M$ and then inspect the corresponding $S,R,D$ rows;
\item limit-seal handoff, requiring the displayed $\RealUp$ row $L$ to be reached only after the regular Cauchy route $M,D,S,R$ has been replayed;
\item completion compatibility, requiring the $\CompletionUniversalPropertyUp$ row $U$ to be read only after the Bishop regular-Cauchy completion source route and the displayed limit seal have both been exposed;
\item ledger non-escape, requiring $P$ and $N$ to export no quotient streams, selected host limits, countable choice, open-cover compactness, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:regular-cauchy-sequential-completeness-carrier}. The visible packet consists of the dyadic ledger $D$, finite windows $S$, regular sequence row $R$, modulus row $M$, limit seal $L$, universal-property row $U$, and the structural rows $H,C,P,N$.

Classifier stability is componentwise. The transport row $H$ preserves the displayed analytic rows and the structural rows, so a classified replacement cannot change the tolerance ledger, stream windows, regular readback, threshold schedule, limit seal, or universal-property compatibility route.

Regular-sequence tail control is forced by the order of the replay row $C$. A tolerance request first reads its threshold from $M$, then inspects the finite windows $S$, the regular rational readback $R$, and the dyadic ledger $D$ attached to that threshold.

The limit-seal handoff and completion compatibility are downstream of the same route. The $\RealUp$ seal $L$ is reached only after $M,D,S,R$ have been displayed, and the row $U$ is then read as the completion-universal compatibility surface attached to that visible source-and-limit pair.

Finally, $P$ and $N$ record only provenance and local naming for the listed rows. Since no excluded coordinate occurs in the carrier, the local NameCert surface is exhausted by the six obligations displayed above.
\end{proof}

\begin{theorem}[RegularCauchySequentialCompleteness limit seal]
\label{thm:regular-cauchy-sequential-completeness-limit-seal}
Let $Q=(D,S,R,M,L,U,H,C,P,N)$ be an accepted $\RegularCauchySequentialCompletenessUp$ carrier. Every real-facing sequential-completeness consumer of $Q$ reaches the displayed limit only through the finite route
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp,\ \BishopRegularCauchyCompletionUp,\ \CompletionUniversalPropertyUp .
$$
The limit seal is the row $L$ read after $M,D,S,R$ and before $U$ is consumed; it is not a selected host limit, quotient representative, countable-choice output, open-cover compactness consequence, or ambient completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Project the accepted carrier $Q$. The only rows available to a real-facing consumer before the limit read are $M,D,S,R$ together with the transport and replay rows that preserve their displayed order.

The consumer first reads the regular Cauchy request through $M$. The threshold supplied by $M$ selects the finite stream windows in $S$, the regular rational readback in $R$, and the dyadic tolerance comparisons in $D$.

Only after that route is displayed can the consumer read $L$ as the $\RealUp$ limit seal. The completion-universal row $U$ is then available as compatibility data for the same visible route, not as a second source of limits.

The excluded objects are absent from the tuple. Hence the limit seal cannot be obtained by quotient streams, host representatives, choice, open covers, or an ambient completeness principle.
\end{proof}

\begin{theorem}[RegularCauchySequentialCompleteness modulus-limit determinacy]
\label{thm:regular-cauchy-sequential-completeness-modulus-limit-determinacy}
Let $Q=(D,S,R,M,L,U,H,C,P,N)$ and $Q'=(D',S',R',M',L',U',H',C',P',N')$ be accepted $\RegularCauchySequentialCompletenessUp$ carriers. Suppose the transport rows display componentwise $\hsame$ comparison between $D$ and $D'$, between $S$ and $S'$, between $R$ and $R'$, and between $M$ and $M'$. Suppose also that $C$ and $C'$ give compatible displayed $\Cont$ replay for the same dyadic tolerance request through those transported rows. Then the two real-facing sequential-completeness reads reach the same displayed limit-seal route before either $U$ or $U'$ is consumed.

Equivalently, the displayed seal comparison is determined by the transported modulus-source route $M,D,S,R$. No quotient stream, selected host limit, countable-choice row, host representative, open-cover compactness argument, or ambient $\RealUp$ completeness coordinate can separate the seal route of $Q$ from the seal route of $Q'$.
\end{theorem}
\begin{proof}
Project both accepted carriers. By \autoref{thm:regular-cauchy-sequential-completeness-namecert-obligations}, classifier stability sees the dyadic ledger, stream-window row, regular rational readback, and modulus row only through componentwise $\hsame$ transport. Thus the displayed source route for the fixed tolerance request is the transported route $M,D,S,R$ on the first carrier and the matching route $M',D',S',R'$ on the second carrier.

The compatible $\Cont$ replay rows preserve the order of that route. The request first reads the modulus threshold, then the finite stream windows, then the regular rational sequence row and the dyadic comparison ledger. The two replays therefore expose the same finite source information before any completion-universal compatibility row is available.

Apply \autoref{thm:regular-cauchy-sequential-completeness-limit-seal} to each carrier. In both reads, the $\RealUp$ seal is reached exactly after the displayed $M,D,S,R$ route and strictly before the corresponding $U$ row is consumed. Since the source route has already been identified by transport and compatible replay, the two reads display the same limit-seal route.

The remaining excluded data are not coordinates of either carrier before the seal. Quotient streams, selected host limits, countable choice, host representatives, open-cover compactness, and ambient $\RealUp$ completeness therefore have no local row by which they could distinguish the two displayed seal routes.
\end{proof}

\begin{theorem}[RegularCauchySequentialCompleteness nonescape]
\label{thm:regular-cauchy-sequential-completeness-nonescape}
Every completion-facing or real-facing read of an accepted $\RegularCauchySequentialCompletenessUp$ carrier $Q=(D,S,R,M,L,U,H,C,P,N)$ is exhausted by the rows $D,S,R,M,L,U,H,C,P,N$. Thus the local packet exports only dyadic tolerances, finite stream windows, regular rational sequence data, regular Cauchy modulus thresholds, a displayed $\RealUp$ limit seal, completion-universal compatibility, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming data.

It exports no quotient streams, selected host limits, countable choice, open-cover compactness, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
The carrier tuple lists every row admitted by the local certificate. A completion-facing or real-facing consumer can therefore obtain only $D,S,R,M,L,U,H,C,P,N$ by projection.

The structural rows do not enlarge the analytic surface. The $\hsame$ row transports already displayed coordinates, the $\Cont$ row replays the same ordered route, and the provenance and naming rows record the finite source of the packet.

Since the excluded objects are not coordinates of the carrier and are not produced by the replay route, no accepted read can escape the displayed regular-Cauchy sequential-completeness boundary.
\end{proof}

\begin{theorem}[RegularCauchySequentialCompleteness scoped kernel route]
\label{thm:regular-cauchy-sequential-completeness-scoped-kernel-route}
Every accepted $\RegularCauchySequentialCompletenessUp$ carrier factors through the displayed L10 finite rows
$$
\DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp \longrightarrow \BishopRegularCauchyCompletionUp \longrightarrow \RealSequentialCompletenessUp \longrightarrow \CompletionUniversalPropertyUp .
$$
The factorization reads the dyadic tolerance rows, finite stream windows, regular rational readback, terminal limit seal, Bishop regular-Cauchy completion route, real-sequential-completeness consumer boundary, and completion-universal handoff in that order. It exports no quotient stream, selected limit, countable-choice witness, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier definition. The available analytic rows are the dyadic ledger $D$, finite windows $S$, regular rational sequence row $R$, modulus row $M$, displayed limit seal $L$, and completion-universal row $U$.

Use the limit-seal theorem to locate the $\RealUp$ read. It places $L$ after the displayed $M,D,S,R$ route and before the completion-universal row is consumed.

Use modulus-limit determinacy and nonescape. These results keep every real-facing read inside the transported finite rows and prevent quotient streams, selected limits, countable choice, and ambient completeness from entering as hidden coordinates.

Finally read the sibling dependencies in the order named in the chapter introduction: DyadicRatCore tolerances, StreamName windows, RegSeqRat readback, RealUp seal, Bishop regular-Cauchy completion, RealSequentialCompleteness boundary, and CompletionUniversalProperty handoff.
\end{proof}

\begin{closurestatus}{\RegularCauchySequentialCompletenessUp}
  \constructivestory{A $\RegularCauchySequentialCompletenessUp$ packet is generated from a DyadicRatCore tolerance ledger, finite StreamName windows, a RegSeqRat regular rational sequence row, a regular Cauchy modulus row, a displayed RealUp limit seal, a CompletionUniversalProperty compatibility row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-sequential-completeness-carrier}, \autoref{thm:regular-cauchy-sequential-completeness-namecert-obligations}, \autoref{thm:regular-cauchy-sequential-completeness-limit-seal}, \autoref{thm:regular-cauchy-sequential-completeness-modulus-limit-determinacy}, and \autoref{thm:regular-cauchy-sequential-completeness-nonescape} seed the finite regular-Cauchy sequential-completeness surface between $\RegSeqRatUp$ data and the displayed $\RealUp$ limit seal.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RegularCauchySequentialCompletenessUp.RegularCauchySequentialCompletenessUpTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter excludes quotient streams, selected host limits, countable choice, open-cover compactness, Real completeness as an ambient principle, Lean verification, and bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, regular-sequence tail control, limit-seal handoff, completion compatibility, and ledger non-escape for BEDC.Derived.RegularCauchySequentialCompletenessUp.}
\end{closurestatus}
