\chapter{A Concrete Naming Certificate for $\RegularCauchyMinimumUp$}
\label{ch:concrete-instances-regular-cauchy-minimum-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyMinimumUp$ packet records the finite Bishop-style route for the lower member of two regular Cauchy real names without importing a host minimum operation or an ambient order-completeness principle. It reads the dyadic arithmetic surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the located comparison modulus of \autoref{ch:concrete-instances-locatedness-modulus-namecert}, and the Archimedean comparison budget of \autoref{ch:concrete-instances-archimedeanreal-namecert}. The certificate gives downstream real-order and completion-facing chapters one finite route for binary lower-bound formation before quotient stream equality, selected limits, countable choice, trichotomy, or ambient $\RealUp$ completeness is available.

\begin{definition}[Regular Cauchy minimum carrier]\label{def:regular-cauchy-minimum-carrier}
A $\RegularCauchyMinimumUp$ carrier is a finite $\BHist$ packet
$$
M=(X,Y,T,L,D,A,B,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two accepted $\RealUp$ rows presented by regular Cauchy names. Each row exposes only its finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, dyadic tolerance ledger, and terminal real seal.
\item $T$ is the dyadic comparison tolerance row. It stores the requested output tolerance, the comparison tolerance used to separate the two names when a side is selected, and the smaller dyadic budget consumed by the exported lower-bound row.
\item $L$ is the $\LocatednessModulusUp$ row. It records the finite located comparison request for the two displayed regular Cauchy names and never supplies a host trichotomy or a global order decision.
\item $D$ is the $\DyadicRatCoreUp$ arithmetic ledger for the two readbacks, the comparison tolerance, and the lower dyadic approximation chosen for the output name.
\item $A$ is the $\ArchimedeanRealUp$ budget row, used only to align dyadic comparison scale, regular Cauchy tail scale, and the requested output tolerance.
\item $B$ is the finite branch ledger. It records whether the displayed located comparison routes the lower-bound output through the left name, through the right name, or through the overlap tolerance when the two windows are indistinguishable at the requested scale.
\item $W$ is the exported regular Cauchy output row. Every window of $W$ is copied from $X$ or $Y$ under the branch ledger $B$ and the tolerance rows $T,L,D,A$.
\item $H$ records componentwise $\hsame$ transport for the two input names, tolerance, locatedness, dyadic arithmetic, Archimedean budget, branch, output, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a lower-bound request through $X,Y,T,L,D,A,B,W,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyMinimumUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\LocatednessModulusUp$, $\ArchimedeanRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyMinimumUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the tuple $X,Y,T,L,D,A,B,W,H,C,P,N$. The carrier has no coordinate for a host minimum function, trichotomy, quotient stream equality, selected limits, countable-choice schedules, ambient real completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyMinimumUp.RegularCauchyMinimumTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy minimum NameCert obligations]\label{thm:regular-cauchy-minimum-namecert-obligations}
For every accepted $\RegularCauchyMinimumUp$ carrier
$$
M=(X,Y,T,L,D,A,B,W,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyMinimumUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two regular Cauchy real rows, tolerance row, locatedness row, dyadic arithmetic ledger, Archimedean budget, branch ledger, output row, transport, replay, provenance, and local name;
\item input regularity, requiring every exported output window to be copied from the displayed regular Cauchy windows of $X$ or $Y$ at the scale fixed by $T,D,A$;
\item located comparison, requiring the side ledger $B$ to be read only after the locatedness row $L$ and the dyadic tolerance row $T$ have been displayed;
\item left-bound exactness, requiring a left-routed branch to expose an output window no larger than the displayed window of $X$ at the requested tolerance;
\item right-bound exactness, requiring a right-routed branch to expose an output window no larger than the displayed window of $Y$ at the requested tolerance;
\item classifier stability, requiring componentwise $\hsame$ transport of $X,Y,T,L,D,A,B,W,C,P,N$ to preserve the accepted lower-bound route;
\item non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no host minimum, trichotomy, quotient stream equality, selected limit, countable choice, ambient Real completeness, Lean verification, or bridge credential.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-minimum-carrier}. Its displayed rows are exactly the two regular Cauchy real inputs, the dyadic tolerance row, locatedness row, dyadic arithmetic ledger, Archimedean budget, branch ledger, output row, and structural rows.

Input regularity follows because $W$ has no independent numeric coordinate. Each exported window is copied from $X$ or $Y$ after the tolerance, locatedness, dyadic, and Archimedean rows fix the scale.

The left-bound and right-bound rows are then read from $B$. A left-routed branch consumes the left input window and the overlap tolerance; a right-routed branch consumes the right input window and the same displayed tolerance surface.

Classifier stability and non-escape are ledger exhaustion. The only permitted transports and replays are $H$ and $C$, and the provenance and naming rows $P,N$ cite no excluded host or quotient object.
\end{proof}

\begin{theorem}[Regular Cauchy minimum left bound]\label{thm:regular-cauchy-minimum-left-bound}
Let $M=(X,Y,T,L,D,A,B,W,H,C,P,N)$ be an accepted $\RegularCauchyMinimumUp$ carrier. Every finite window exported by $W$ is a displayed lower-bound window for the left input row $X$ at the tolerance recorded in $T$. The witness is read entirely from the branch ledger $B$, the locatedness row $L$, the dyadic arithmetic ledger $D$, the Archimedean budget $A$, the $\hsame$ transport $H$, and the replay row $C$.
\end{theorem}
\begin{proof}
Project the displayed output window from $W$ and inspect the corresponding branch row in $B$.

In a left-routed branch, the output window is copied from $X$, so the claimed left-bound row is the reflexive displayed comparison transported by $H$ and replayed by $C$.

In a right-routed or overlap branch, the locatedness row $L$ supplies the finite comparison certificate at the dyadic scale fixed by $T,D,A$. The output window is copied from $Y$ only under that certificate, so the same ledger gives the displayed lower-bound comparison against $X$.

No other comparison source exists in the carrier. The proof is therefore exhausted by $B,L,T,D,A,H,C$.
\end{proof}

\begin{theorem}[Regular Cauchy minimum right bound]\label{thm:regular-cauchy-minimum-right-bound}
Let $M=(X,Y,T,L,D,A,B,W,H,C,P,N)$ be an accepted $\RegularCauchyMinimumUp$ carrier. Every finite window exported by $W$ is a displayed lower-bound window for the right input row $Y$ at the tolerance recorded in $T$. The witness is read entirely from the branch ledger $B$, the locatedness row $L$, the dyadic arithmetic ledger $D$, the Archimedean budget $A$, the $\hsame$ transport $H$, and the replay row $C$.
\end{theorem}
\begin{proof}
Project the displayed output window from $W$ and inspect its branch row in $B$.

In a right-routed branch, the output window is copied from $Y$, so the claimed right-bound row is the reflexive displayed comparison transported by $H$ and replayed by $C$.

In a left-routed or overlap branch, the locatedness row $L$ supplies the finite comparison certificate at the dyadic scale fixed by $T,D,A$. The output window is copied from $X$ only under that certificate, so the same ledger gives the displayed lower-bound comparison against $Y$.

The carrier contains no independent host order proof. Thus the right-bound witness is exactly the local projection of $B,L,T,D,A,H,C$.
\end{proof}

\begin{theorem}[Regular Cauchy minimum classifier stability]\label{thm:regular-cauchy-minimum-classifier-stability}
If two accepted $\RegularCauchyMinimumUp$ carriers
$$
M=(X,Y,T,L,D,A,B,W,H,C,P,N)
$$
and
$$
M'=(X',Y',T',L',D',A',B',W',H',C',P',N')
$$
are componentwise $\hsame$ on the two input names, tolerance, locatedness, dyadic arithmetic, Archimedean budget, branch ledger, output row, replay, provenance, and local naming row, then their classifiers agree. In particular, every accepted lower-bound window in $W$ is transported to the corresponding accepted lower-bound window in $W'$ without adding a host minimum or quotient-stream equality.
\end{theorem}
\begin{proof}
Unfold the classifier described in \autoref{def:regular-cauchy-minimum-carrier}. It reads only $X,Y,T,L,D,A,B,W,H,C,P,N$.

The assumed componentwise $\hsame$ rows identify each coordinate with its primed counterpart. Transport along those rows preserves the side ledger, the copied output window, and the displayed dyadic comparison scale.

Since neither classifier has a hidden coordinate, there is no remaining source from which disagreement could arise. The transported packet is accepted exactly when the original packet is accepted.
\end{proof}

\begin{theorem}[Regular Cauchy minimum non-escape]\label{thm:regular-cauchy-minimum-nonescape}
Every accepted $\RegularCauchyMinimumUp$ carrier exports only the finite lower-bound route described by \autoref{def:regular-cauchy-minimum-carrier}. No consumer of the packet can recover a host minimum function, trichotomy of real names, quotient stream equality, selected limit, countable-choice schedule, ambient $\RealUp$ completeness principle, Lean verification, or bridge checking credential.
\end{theorem}
\begin{proof}
Read the carrier coordinate by coordinate. Numeric data are confined to the two input rows, the tolerance row, the locatedness row, the dyadic ledger, the Archimedean budget, the branch ledger, and the output row.

Transport and replay are confined to $H$ and $C$. Provenance and local naming are confined to $P$ and $N$, and those rows cite only the finite BEDC names listed in the carrier.

The excluded principles have no coordinate, no provenance entry, and no replay edge. Therefore a consumer can inspect the displayed lower-bound certificate but cannot escape to any host or quotient object.
\end{proof}

\closureat{RegularCauchyMinimumUp}{seedStr}

\begin{closurestatus}{\RegularCauchyMinimumUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-minimum-carrier}, \autoref{thm:regular-cauchy-minimum-namecert-obligations}, \autoref{thm:regular-cauchy-minimum-left-bound}, \autoref{thm:regular-cauchy-minimum-right-bound}, \autoref{thm:regular-cauchy-minimum-classifier-stability}, and \autoref{thm:regular-cauchy-minimum-nonescape} seed a finite lower-bound route for two regular Cauchy real names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host minimum, trichotomy, quotient stream equality, selected limits, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, input regularity, located comparison, left-bound exactness, right-bound exactness, classifier stability, and non-escape proofs for BEDC.Derived.RegularCauchyMinimumUp.}
  \constructivestory{A $\RegularCauchyMinimumUp$ packet is generated from two regular Cauchy Real rows, a dyadic comparison tolerance, a LocatednessModulus row, a DyadicRatCore arithmetic ledger, an ArchimedeanReal budget, a branch ledger, an output regular Cauchy row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
