\chapter{A Concrete Naming Certificate for $\RegularCauchyLocationWitnessUp$}
\label{ch:concrete-instances-regular-cauchy-location-witness-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyLocationWitnessUp$ packet records the finite location witness by which a regular Cauchy rational name may be consumed as a located real-name route. It sits over the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the sequence-level located Cauchy surface of \autoref{ch:concrete-instances-locatedcauchy-namecert}, and the filter-level located witness rows of \autoref{ch:concrete-instances-located-cauchy-filter-namecert}. The certificate supplies the missing sequence-level location surface for later $\RealUp$ consumers without asserting Dedekind cuts, quotient streams, selected limits, countable choice, real trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy location witness carrier]
\label{def:regular-cauchy-location-witness-carrier}
A $\RegularCauchyLocationWitnessUp$ carrier is a finite $\BHist$ packet
$$
L=(R,S,D,W,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the regular source row, namely the $\RegSeqRatUp$ regular rational name whose finite windows are being located.
\item $S$ is the finite window schedule, namely the $\StreamNameUp$ row that exposes exactly the inspected windows of $R$.
\item $D$ is the dyadic tolerance ledger, recording requested radii, comparison budgets, endpoint approximants, and window tolerances.
\item $W$ is the location-witness row, recording for each displayed dyadic cut request a finite left-or-right locatedness witness over the windows selected by $S$ and the tolerances in $D$.
\item $E$ is the $\RealUp$ seal boundary, reachable only after $R,S,D,W$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the regular source, schedule, dyadic ledger, location witness, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a location request through $R,S,D,W,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyLocationWitnessUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\LocatedCauchyUp$, $\LocatedCauchyFilterUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyLocationWitnessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,S,D,W,E,H,C,P,N$. The carrier contains no Dedekind cut, quotient stream equality, real trichotomy branch, countable-choice selector, selected limit, ambient $\RealUp$ completeness theorem, Lean verification credential, or bridge checking datum.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyLocationWitnessUp.TasteGate.RegularCauchyLocationWitnessTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy location witness NameCert obligations]
\label{thm:regular-cauchy-location-witness-namecert-obligations}
For every accepted $\RegularCauchyLocationWitnessUp$ carrier
$$
L=(R,S,D,W,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyLocationWitnessUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the regular source row, finite window schedule, dyadic tolerance ledger, location-witness row, $\RealUp$ seal boundary, transport, replay, provenance, and local name;
\item regular-source exposure, requiring every location request to read the $\RegSeqRatUp$ source row $R$ only through the displayed schedule $S$;
\item dyadic-budget exactness, requiring each locatedness comparison to consume the radius, endpoint, and tolerance data stored in $D$ before the witness row $W$ is inspected;
\item witness routing, requiring $W$ to record only finite left-or-right locatedness rows over the windows selected by $S$ and the dyadic budget supplied by $D$;
\item seal non-escape, requiring every $\RealUp$ read to remain downstream of $R,S,D,W$;
\item structural stability, requiring $H,C,P,N$ to transport, replay, source, and name exactly the displayed route and no off-packet completeness or choice object.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier from \autoref{def:regular-cauchy-location-witness-carrier}. The analytic rows are exactly the regular rational source, the finite schedule, the dyadic tolerance ledger, the location witness, and the terminal seal boundary.

Regular-source exposure is forced by the schedule row. A location request cannot inspect $R$ directly; it must pass through the finite windows named by $S$.

The dyadic-budget and witness rows are then read together. The ledger $D$ supplies the radius, endpoint, and tolerance data for the displayed cut request, and $W$ records the finite locatedness witness over those same scheduled windows.

Finally, seal non-escape and structural stability are componentwise. The seal row $E$ is reached only after $R,S,D,W$, while $H,C,P,N$ preserve, replay, source, and name that same route. Since no excluded object is a coordinate of the packet, the local certificate has no place from which to export Dedekind cuts, quotient streams, trichotomy, choice, selected limits, ambient completeness, Lean verification, or bridge checking.
\end{proof}

\begin{theorem}[Regular Cauchy location witness regular readback]
\label{thm:regular-cauchy-location-witness-regular-readback}
Let
$$
L=(R,S,D,W,E,H,C,P,N)
$$
be an accepted $\RegularCauchyLocationWitnessUp$ carrier. Every location read of $L$ factors through the displayed regular-Cauchy route
$$
R \longmapsto S \longmapsto D \longmapsto W
$$
before any $\RealUp$ seal or structural row is inspected.
\end{theorem}
\begin{proof}
Begin with a location read. Carrier admission supplies $R$ as the only regular rational source row, so no second stream representative or quotient stream can be selected.

The read then passes through $S$. This schedule determines the finite windows on which the regular source is inspected, and it is the only window source available to the packet.

Next the read consumes $D$ and $W$. The dyadic ledger fixes the tolerance and endpoint budget, while the witness row records the finite locatedness decision over the scheduled windows.

Only after this route is displayed can the read reach $E$ or the structural rows $H,C,P,N$. Thus every location read is a regular-Cauchy readback route rather than a host-level located real construction.
\end{proof}

\begin{theorem}[Regular Cauchy location witness Real seal non-escape]
\label{thm:regular-cauchy-location-witness-real-seal-nonescape}
For every accepted $\RegularCauchyLocationWitnessUp$ carrier $L=(R,S,D,W,E,H,C,P,N)$, the exported $\RealUp$ seal $E$ is read only as the terminal boundary of the displayed finite route through $R,S,D,W,H,C,P,N$. It exports no Dedekind cuts, quotient stream equality, real trichotomy, countable-choice selector, selected limit, ambient Real completeness theorem, Lean verification, or bridge checking datum.
\end{theorem}
\begin{proof}
Project the seal row from the carrier. The row $E$ is listed after the regular source, schedule, dyadic ledger, and witness rows, so a seal-facing consumer has no direct entry to $E$.

Use \autoref{thm:regular-cauchy-location-witness-regular-readback}. Any seal-facing location route first reads $R,S,D,W$, and those rows exhaust the finite analytic data available to the packet.

The structural rows preserve only this route. Transport $H$, replay $C$, provenance $P$, and local naming $N$ do not add new analytic coordinates; they keep the same displayed packet available under componentwise comparison and continuation.

The excluded principles are absent from the carrier inventory and from the provenance row. Therefore the terminal seal remains a finite located regular-Cauchy boundary, not a proof of Dedekind completeness, quotient equality, trichotomy, choice, selected limits, Lean verification, or bridge checking.
\end{proof}

\closureat{RegularCauchyLocationWitnessUp}{seedStr}

\begin{closurestatus}{\RegularCauchyLocationWitnessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-location-witness-carrier}, \autoref{thm:regular-cauchy-location-witness-namecert-obligations}, \autoref{thm:regular-cauchy-location-witness-regular-readback}, and \autoref{thm:regular-cauchy-location-witness-real-seal-nonescape} seed the finite location-witness route from regular rational source rows through StreamName windows, DyadicRatCore tolerances, displayed locatedness witnesses, and the terminal Real seal.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RegularCauchyLocationWitnessUp.TasteGate.RegularCauchyLocationWitnessTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Dedekind cuts, quotient streams, real trichotomy, countable choice, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, regular-source exposure, dyadic-budget exactness, witness routing, regular readback, Real-seal non-escape, and structural stability for BEDC.Derived.RegularCauchyLocationWitnessUp.}
  \constructivestory{A $\RegularCauchyLocationWitnessUp$ packet is generated from a RegSeqRat regular source row, finite StreamName windows, a DyadicRatCore tolerance ledger, displayed locatedness witnesses, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
