\chapter{A Concrete Naming Certificate for $\CesaroConvergenceUp$}
\label{ch:concrete-instances-cesaro-convergence-namecert}
\origin{human}

Following Hardy's classical treatment of Cesaro summability, the $\CesaroConvergenceUp$ packet records ordinary convergence of the displayed Cesaro means as a BEDC finite-window certificate over regular real-sequence data. It consumes the finite averaging surface of \autoref{ch:concrete-instances-hardy-cesaro-mean-namecert}, keeps the quotient-tail comparison discipline of \autoref{ch:concrete-instances-stolz-cesaro-namecert} available as a sibling route, routes every transformed read through the regular rational interface of \autoref{ch:concrete-instances-regseqrat-namecert}, and reaches the terminal real-name seal only through \autoref{ch:concrete-instances-real-namecert}. The chapter names the carrier that a convergence consumer may inspect; it does not import a host convergence theorem or an ambient limit object.

\begin{definition}[Cesaro convergence carrier]\label{def:cesaro-convergence-carrier}
A $\CesaroConvergenceUp$ carrier is a finite $\BHist$ packet
$$
C=(S,M,A,L,R,E,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source real-sequence row, exposed only through the finite $\StreamNameUp$ windows requested by the current convergence tolerance.
\item $M$ is the $\HardyCesaroMeanUp$ row carrying the displayed prefix sums, unary denominator rows, dyadic division budgets, and finite Cesaro mean windows generated from $S$.
\item $A$ is the finite averaging ledger, recording for each inspected tolerance the source windows, prefix rows, denominator rows, and dyadic error budgets used by the displayed Cesaro means.
\item $L$ is the convergence-window ledger, containing the finite tail requests that classify the Cesaro mean rows as a regular real sequence.
\item $R$ is the $\RegSeqRatUp$ handoff row reached from $M,A,L$ before any completed real-name seal is read.
\item $E$ is the $\RealUp$ seal row reached only after the source, Cesaro mean, averaging ledger, convergence-window ledger, and regular handoff rows have been displayed.
\item $H$ stores componentwise $\hsame$ transports for the sequence source, Cesaro mean rows, averaging ledger, convergence ledger, regular handoff, real seal, continuation rows, provenance, and local naming.
\item $T$ stores displayed $\Cont$ routes from source-window reads to Cesaro mean rows, from Cesaro mean rows to convergence-window classification, from that classification to $R$, and from $R$ to $E$.
\item $P$ is the $\Pkg$ provenance over $\CesaroConvergenceUp$, $\HardyCesaroMeanUp$, $\StolzCesaroUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CesaroConvergenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,M,A,L,R,E,H,T,P,N$. It has no coordinate for ordinary pointwise convergence of the source sequence, a host limit, quotient stream equality, a choice-selected subsequence, trichotomy, or ambient real completeness.
\end{definition}
\leanchecked{BEDC.Derived.CesaroConvergenceUp.TasteGate.CesaroConvergenceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cesaro convergence NameCert obligations]\label{thm:cesaro-convergence-namecert-obligations}
For every accepted $\CesaroConvergenceUp$ carrier $C=(S,M,A,L,R,E,H,T,P,N)$, the local $\NameCert_{\CesaroConvergenceUp}$ surface consists exactly of the following six finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source row, Hardy--Cesaro mean row, averaging ledger, convergence-window ledger, regular handoff, real seal, transport, continuation, provenance, and naming rows;
\item mean-window classification, requiring each accepted Cesaro mean read to be generated by $M$ from the finite source windows and averaging ledger $A$;
\item stability, requiring the displayed $\hsame$ transports $H$ and $\Cont$ routes $T$ to preserve the same source, averaging, convergence-window, regular handoff, and real-seal rows;
\item $\RegSeqRatUp$ handoff, requiring every accepted convergence read to pass through $R$ after $M,A,L$ have been displayed;
\item $\RealUp$ seal factorization, requiring the seal row $E$ to consume only the regular handoff obtained from the displayed Cesaro averaging route;
\item ledger non-escape, excluding ordinary pointwise convergence of $S$, host limits, quotient stream equality, choice-selected subsequences, and any detached real-completeness coordinate.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cesaro-convergence-carrier}. Carrier admission is exactly the displayed packet $S,M,A,L,R,E,H,T,P,N$, so the certificate has no free coordinate for a source-sequence limit or an external convergence oracle.

Mean-window classification is supplied by the order of the rows. The source windows in $S$ feed the $\HardyCesaroMeanUp$ row $M$, and $A$ records the finite averaging ledger that produced each displayed Cesaro mean from prefix sums, denominator rows, and dyadic budgets.

The convergence side is then forced through $L$ and $R$. The ledger $L$ records the finite tail requests witnessing regularity of the Cesaro mean sequence, while $R$ is the only $\RegSeqRatUp$ handoff reachable from those requests before any real seal is visible.

Finally, $E$ is downstream of $R$, and $H,T,P,N$ merely transport, replay, source, and name the same route. Since no listed row stores ordinary pointwise convergence, a host limit, quotient stream equality, a selected subsequence, or ambient completeness, the six obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cesaro convergence RegSeqRat handoff]\label{thm:cesaro-convergence-regseqrat-handoff}
Every accepted $\CesaroConvergenceUp$ read reaches $\RegSeqRatUp$ through the $\HardyCesaroMeanUp$ row and the displayed averaging ledger before the $\RealUp$ seal is available. More precisely, for every accepted packet $C=(S,M,A,L,R,E,H,T,P,N)$, a completion-facing consumer can reach $E$ only along the route
$$
S \longmapsto M \longmapsto A \longmapsto L \longmapsto R \longmapsto E \longmapsto (H,T,P,N).
$$
The sibling $\StolzCesaroUp$ route may certify compatible quotient-tail estimates in $P$, but it does not bypass $M,A,L,R$ for the Cesaro-convergence read.
\end{theorem}
\begin{proof}
Begin with a completion-facing read of $C$. By \autoref{def:cesaro-convergence-carrier}, the read first exposes the source row $S$ only as finite stream windows.

The next analytic surface is $M$. This is the $\HardyCesaroMeanUp$ packet of \autoref{ch:concrete-instances-hardy-cesaro-mean-namecert}; it supplies the finite prefix-sum, denominator, dyadic-division, and Cesaro mean rows. The averaging ledger $A$ records the same rows as the local route consumed by the convergence classifier.

The tail classifier then reads $L$ and only then reaches the $\RegSeqRatUp$ handoff $R$. The sibling $\StolzCesaroUp$ edge named in $P$ can provide quotient-tail compatibility data, but the displayed route for this carrier still passes through the Cesaro mean row and averaging ledger before $R$.

The $\RealUp$ seal $E$ is downstream of $R$. The structural rows $H,T,P,N$ preserve and name the route, so a consumer that reaches $E$ has already consumed $S,M,A,L,R$ and receives no ordinary pointwise convergence witness, host limit, quotient stream equality, selected subsequence, or ambient completeness principle.
\end{proof}

\falsifiablePrediction{Every $\CesaroConvergenceUp$ Real-facing read factors through source sequence windows, a HardyCesaroMean row, a finite averaging ledger, a convergence-window ledger, RegSeqRat handoff, RealUp seal, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{hardycesaromean, stolzcesaro, streamname, regseqrat, dyadicratcore, real: $\CesaroConvergenceUp$ is not bijective to any listed sibling because it jointly carries a source sequence row, Hardy--Cesaro mean rows, an averaging ledger, a convergence-window ledger, RegSeqRat handoff, Real seal, transport, continuation, provenance, and local naming.}

\closureat{CesaroConvergenceUp}{seedStr}

\begin{closurestatus}{\CesaroConvergenceUp}
  \constructivestory{A $\CesaroConvergenceUp$ packet is generated from a source real-sequence row, finite HardyCesaroMean averaging rows, an averaging ledger, convergence-window ledger, RegSeqRat handoff, RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cesaro-convergence-carrier}, \autoref{thm:cesaro-convergence-namecert-obligations}, and \autoref{thm:cesaro-convergence-regseqrat-handoff} seed the finite Cesaro-convergence surface from regular real-sequence windows to the Real-facing seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ordinary pointwise convergence, host limits, quotient stream equality, choice-selected subsequences, Lean verification, bridge checking, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, mean-window classification, stability, RegSeqRat handoff, RealUp seal factorization, ledger non-escape, and TasteGate field faithfulness for BEDC.Derived.CesaroConvergenceUp.}
\end{closurestatus}
