\chapter{Compact Baire NameCert Construction}
\label{ch:concrete-instances-compact-baire-namecert}
\origin{human}

Beginning from the Baire category theorem for complete metric spaces, as developed by Baire, Oxtoby, and Bishop--Bridges, the $\CompactBaireUp$ packet records the finite BEDC route by which a compact metric certificate may feed a dense-open Baire certificate without importing open-cover compactness or host intersections. It reads the compact metric carrier of \autoref{ch:concrete-instances-compactmetric-namecert}, the dense-open handoff of \autoref{ch:concrete-instances-bairecategory-namecert}, the enumerated dense surface of \autoref{ch:concrete-instances-countable-dense-subset-namecert}, the complete-metric witness of \autoref{ch:concrete-instances-completemetric-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}. The chapter names the compact-metric Baire consequence as certificate composition, not as a host theorem about arbitrary intersections.

\begin{definition}[Compact Baire carrier]
\label{def:compact-baire-carrier}
A $\CompactBaireUp$ carrier is a finite $\BHist$ packet
$$
K=(X,B,D,C,S,R,T,H,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\CompactMetricUp$ row, exposing the metric carrier, total-bounded finite-net data, and complete-limit route that will be inspected by the Baire argument.
\item $B$ is the $\BaireCategoryUp$ dense-open row, restricted to the displayed compact-metric source row $X$.
\item $D$ is the $\CountableDenseSubsetUp$ row used to enumerate the finite dense probes that a scheduled dense-open request may read.
\item $C$ is the $\CompleteMetricUp$ handoff row inherited from the compact metric certificate and presented as the only completion route visible to the Baire row.
\item $S$ is the $\StreamNameUp$ schedule controlling which compact probes, dense-open rows, countable dense indices, and completion windows may be inspected.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational tolerance and radius comparisons used by the finite dense-open route.
\item $T$ is the compact Baire trace ledger, recording the finite passage from compact-metric data through the complete-metric handoff and dense-open route to the displayed readback.
\item $H$ records componentwise $\hsame$ transport for $X,B,D,C,S,R,T$ and the structural rows.
\item $P$ is the $\Pkg$ provenance over $\CompactBaireUp$, $\CompactMetricUp$, $\BaireCategoryUp$, $\CountableDenseSubsetUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactBaireUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It contains no open-cover compactness object, countable-choice selector, host set intersection, ambient Real completeness row, Lean verification credential, or standard bridge credential.
\end{definition}
\leanchecked{BEDC.Derived.CompactBaireUp.CompactBaireTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Compact Baire NameCert obligations]
\label{thm:compact-baire-namecert-obligations}
For every accepted $\CompactBaireUp$ carrier $K=(X,B,D,C,S,R,T,H,P,N)$, the local $\NameCert_{\CompactBaireUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the compact metric row, Baire dense-open row, countable dense row, complete-metric handoff, stream schedule, regular rational readback, trace ledger, transport, provenance, and local naming;
\item compact-source exposure, requiring every dense-open and finite-probe read to enter through the same $\CompactMetricUp$ row $X$;
\item complete-metric handoff, requiring the Baire row to consume the inherited $\CompleteMetricUp$ route $C$ rather than an ambient completion principle;
\item dense-open finite routing, requiring the $\BaireCategoryUp$ row $B$ to use only the displayed schedule $S$, dense row $D$, readback row $R$, and trace ledger $T$;
\item nonescape, excluding open-cover compactness, countable choice, host set intersections, ambient Real completeness, Lean verification, and bridge checking.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-baire-carrier}. The accepted tuple displays exactly the compact metric row, Baire dense-open row, countable dense row, complete-metric handoff, stream schedule, regular rational readback, trace ledger, transport, provenance, and local name.

Compact-source exposure is forced by $X$. The dense-open row $B$, dense index row $D$, complete handoff $C$, schedule $S$, and readback $R$ are all presented downstream of the same compact metric certificate.

The complete-metric handoff is the row $C$. Since $C$ is inherited from the compact metric certificate, the packet has no coordinate from which an ambient completion theorem or separate Real-completeness principle can be selected.

Dense-open finite routing is read from $B,S,R,T$. The route names finite windows, regular rational comparisons, and the compact Baire trace ledger before any dense-open conclusion is exported.

Finally, $H,P,N$ transport, source, and name only the displayed rows. Hence the carrier exports no open-cover compactness object, countable-choice selector, host set intersection, ambient Real completeness row, Lean verification credential, or bridge credential.
\end{proof}

\begin{theorem}[Compact Baire complete metric handoff]
\label{thm:compact-baire-complete-metric-handoff}
Let $K=(X,B,D,C,S,R,T,H,P,N)$ be an accepted $\CompactBaireUp$ carrier. Every Baire read exported by $K$ reaches $\BaireCategoryUp$ only after the compact metric row $X$ has exposed its inherited $\CompleteMetricUp$ handoff $C$.
\end{theorem}
\begin{proof}
Read the carrier from its source row. The compact metric coordinate $X$ is the first row that can supply the metric carrier, total-bounded finite-net surface, and complete-limit route.

The Baire row $B$ is attached to that same source. Its complete-metric requirement is not stored independently; it is the displayed row $C$ inherited from $X$.

Thus any Baire read accepted by the packet passes through $X$ and $C$ before consuming the dense-open rows. The remaining rows $S,R,T,H,P,N$ only schedule, read back, trace, transport, source, and name that route.
\end{proof}

\begin{theorem}[Compact Baire dense-open finite route]
\label{thm:compact-baire-dense-open-finite-route}
Every dense-open request accepted by a $\CompactBaireUp$ carrier factors through the displayed finite route
$$
\CompactMetricUp \longmapsto \CompleteMetricUp \longmapsto \BaireCategoryUp \longmapsto \CountableDenseSubsetUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp .
$$
The route records compact-source admission, completion handoff, dense-open refinement, countable dense probing, scheduled windows, and rational readback before the local name is exported.
\end{theorem}
\begin{proof}
Begin with a dense-open request. Carrier admission sends the request first to $X$, and \autoref{thm:compact-baire-complete-metric-handoff} identifies the displayed completion row $C$ as the only complete-metric route available to the Baire read.

The dense-open step is the row $B$. It is read with the countable dense row $D$, so the request sees only displayed finite probes rather than a choice-selected dense subset.

The schedule and readback are then supplied by $S$ and $R$. The trace ledger $T$ records the same compact-source, completion, dense-open, dense-probe, window, and rational-readback route, while $H,P,N$ transport, source, and name it.
\end{proof}

\begin{theorem}[Compact Baire nonescape boundary]
\label{thm:compact-baire-nonescape-boundary}
For an accepted $\CompactBaireUp$ carrier $K=(X,B,D,C,S,R,T,H,P,N)$, every exported comparison, replay, provenance read, and local name is exhausted by the displayed rows $X,B,D,C,S,R,T,H,P,N$. In particular, the packet exports no open-cover compactness object, countable-choice selector, host set intersection, ambient Real completeness theorem, Lean verification credential, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted carrier. The classifier compares two packets only through the displayed compact metric, Baire, countable dense, complete-metric, stream, regular-rational, trace, transport, provenance, and local naming rows.

The possible escape points are exactly the compactness, density, completion, and dense-open interfaces. The compactness row $X$ is read as the $\CompactMetricUp$ certificate of \autoref{ch:concrete-instances-compactmetric-namecert}; the complete row $C$ is its displayed completion handoff; the dense row $D$ is the finite index surface of \autoref{ch:concrete-instances-countable-dense-subset-namecert}; and the Baire row $B$ is the dense-open route of \autoref{ch:concrete-instances-bairecategory-namecert}.

None of these coordinates stores an open-cover compactness object, countable-choice selector, host set intersection, ambient Real completeness theorem, Lean verification credential, or bridge credential. The structural rows only replay and name the same route, so no exported read can leave the displayed boundary.
\end{proof}

\closureat{CompactBaireUp}{seedStr}

\begin{closurestatus}{\CompactBaireUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-baire-carrier}, \autoref{thm:compact-baire-namecert-obligations}, \autoref{thm:compact-baire-complete-metric-handoff}, \autoref{thm:compact-baire-dense-open-finite-route}, and \autoref{thm:compact-baire-nonescape-boundary} seed the compact-metric Baire certificate route over displayed compactness, completeness, countable dense probing, dense-open refinement, finite windows, and regular rational readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, countable choice, host set intersections, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-source exposure, complete-metric handoff, dense-open finite routing, trace exactness, and nonescape proofs for BEDC.Derived.CompactBaireUp.}
  \constructivestory{A $\CompactBaireUp$ packet is generated from a $\CompactMetricUp$ row, a $\BaireCategoryUp$ dense-open row, a $\CountableDenseSubsetUp$ dense-probe row, an inherited $\CompleteMetricUp$ handoff, $\StreamNameUp$ scheduling, $\RegSeqRatUp$ readback, a trace ledger, componentwise transport, package provenance, and a local $\NameCert$ row.}
\end{closurestatus}
