\chapter{A Concrete Naming Certificate for $\BishopIntervalNestLimitUp$}
\label{ch:concrete-instances-bishop-interval-nest-limit-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopIntervalNestLimitUp$ packet records the finite nested-interval limit route through \autoref{ch:concrete-instances-nestedinterval-namecert}, \autoref{ch:concrete-instances-nesteddyadicinterval-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-real-namecert}, and \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}. The packet gives L10 Real and Completion work a displayed induction-style handoff from nested interval data to a terminal Real seal, while remaining below any claim of general Heine--Borel compactness, selected intersection points, quotient stream equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop interval-nest limit carrier]
\label{def:bishop-interval-nest-limit-carrier}
A $\BishopIntervalNestLimitUp$ carrier is a finite $\BHist$ packet
$$
L=(I,D,S,R,E,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite nested-interval induction row. It records the inspected prefix, the containment step from each displayed interval to its predecessor, and the nonempty interval surface inherited from $\NestedIntervalUp$.
\item $D$ is the $\NestedDyadicIntervalUp$ and $\DyadicRatCoreUp$ endpoint ledger used to read the inspected interval endpoints at the requested dyadic scales.
\item $S$ is the $\StreamNameUp$ schedule row. It exposes only the finite interval-prefix observations and endpoint windows that the induction row permits.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the scheduled endpoint observations and the shrinking-width ledger.
\item $E$ is the terminal $\RealUp$ seal reached only after $I,D,S,R$ have been displayed.
\item $M$ is the Bishop regular Cauchy completion handoff row. It records that the same $I,D,S,R,E$ route is the one consumed by $\BishopRegularCauchyCompletionUp$.
\item $H$ records componentwise $\hsame$ transport for the interval induction row, endpoint ledger, stream schedule, regular rational readback, Real seal, completion handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a nested-interval request through $I,D,S,R,E,M$.
\item $P$ is the $\Pkg$ provenance over $\BishopIntervalNestLimitUp$, $\NestedIntervalUp$, $\NestedDyadicIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRegularCauchyCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopIntervalNestLimitUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,D,S,R,E,M,H,C,P,N$. The carrier contains no general Heine--Borel compactness row, selected intersection point, quotient stream equality, countable-choice selector, ambient $\RealUp$ completeness datum, host real equality, or bridge credential.
\end{definition}
\leanchecked{BEDC.Derived.BishopIntervalNestLimitUp.BishopIntervalNestLimitTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Bishop interval-nest limit NameCert obligations]
\label{thm:bishop-interval-nest-limit-namecert-obligations}
For every accepted $\BishopIntervalNestLimitUp$ carrier
$$
L=(I,D,S,R,E,M,H,C,P,N),
$$
the local $\NameCert_{\BishopIntervalNestLimitUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed nested-interval induction row, dyadic endpoint ledger, stream schedule, regular rational readback, Real seal, Bishop regular Cauchy completion handoff, transport, replay, provenance, and local naming row;
\item induction-step exposure, requiring every interval read to be one of the displayed prefix rows of $I$ and every successor read to pass through the displayed containment step;
\item dyadic endpoint exactness, requiring $D$ to supply the endpoint and shrinking-width comparisons used by the scheduled windows;
\item stream and regular readback discipline, requiring $S$ and $R$ to reuse the same displayed prefix and endpoint ledger rather than selecting a second nested chain or regular sequence;
\item Real-seal handoff, requiring $E$ to be reached only after the nested, dyadic, stream, and regular rational rows have been projected;
\item completion-interface non-escape, requiring $M,H,C,P,N$ to transport, replay, source, and name no general Heine--Borel compactness row, selected intersection point, quotient stream equality, countable-choice selector, ambient Real completeness datum, host real equality, or bridge credential.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:bishop-interval-nest-limit-carrier}. The accepted packet displays exactly the interval induction row, dyadic endpoint ledger, stream schedule, regular rational readback, Real seal, completion handoff, and the structural rows.

The induction-step exposure clause is forced by $I$. A consumer can inspect only the finite prefix already present in the packet, and each displayed successor interval is read together with its containment step into the preceding interval.

Dyadic endpoint exactness is then forced by $D$. The endpoint and shrinking-width comparisons are the only numerical rows available to the schedule, so the packet cannot introduce an external point selector or compactness witness.

The rows $S$ and $R$ are downstream of the same displayed prefix and endpoint ledger. They schedule finite observations and repack them as regular rational readback without replacing the nested chain by a second representative.

Finally, $E,M,H,C,P,N$ close the route. The Real seal and completion handoff are reached only after $I,D,S,R$, while the structural rows transport, replay, source, and name the same finite data. Since no excluded coordinate occurs in the carrier, the local NameCert surface has exactly the listed obligations.
\end{proof}

\begin{theorem}[Bishop interval-nest limit convergence route]
\label{thm:bishop-interval-nest-limit-convergence-route}
Let $L=(I,D,S,R,E,M,H,C,P,N)$ be an accepted $\BishopIntervalNestLimitUp$ carrier. Every Real-facing or completion-facing read exported by $L$ factors through the induction route
$$
I\longmapsto D\longmapsto S\longmapsto R\longmapsto E\longmapsto M
$$
before it can inspect the transport, replay, provenance, or local naming rows. The route is a finite nested-interval handoff into the $\RegSeqRatUp$ readback and the terminal $\RealUp$ seal.
\end{theorem}
\begin{proof}
Begin with a Real-facing or completion-facing read of $L$. The carrier gives no source row before the displayed nested-interval induction row $I$.

The read then projects the dyadic endpoint ledger $D$. This fixes the endpoint observations and shrinking-width comparisons that the later schedule may use.

Next the read passes through $S$ and $R$. The schedule exposes only finite interval-prefix windows, and the regular rational row repacks those same observations as the Cauchy-facing readback.

Only after this route has been displayed can the read reach the Real seal $E$ and the Bishop regular Cauchy completion handoff $M$. The remaining rows $H,C,P,N$ preserve and name that route, so every exported read factors through the displayed induction chain.
\end{proof}

\begin{theorem}[Bishop interval-nest limit nonescape]
\label{thm:bishop-interval-nest-limit-nonescape}
For an accepted $\BishopIntervalNestLimitUp$ carrier $L=(I,D,S,R,E,M,H,C,P,N)$, every exported comparison, replay, provenance read, completion handoff, or local name is exhausted by the displayed rows $I,D,S,R,E,M,H,C,P,N$. In particular, the packet exports no general Heine--Borel compactness theorem, selected intersection point, quotient stream equality, countable-choice selector, host real equality, ambient $\RealUp$ completeness theorem, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted packet. Its classifier compares carriers only through the displayed interval induction row, endpoint ledger, schedule, regular readback, Real seal, completion handoff, and structural rows.

The comparison-sensitive rows are $M,H,C,P,N$. The completion handoff records the same finite route into the Bishop regular Cauchy completion surface, transport is componentwise, replay follows the displayed request path, provenance names the same source chapters, and the local NameCert row names only this packet.

Since no accepted coordinate stores a compactness theorem, an intersection selector, quotient stream equality, choice data, host real equality, ambient Real completeness, or a bridge credential, no exported comparison or replay can use such a row. The packet therefore remains an induction-style nested-interval handoff rather than a completeness assertion.
\end{proof}

\closureat{BishopIntervalNestLimitUp}{seedStr}

\begin{closurestatus}{\BishopIntervalNestLimitUp}
  \constructivestory{A $\BishopIntervalNestLimitUp$ packet is generated from a finite nested-interval induction row, a nested dyadic endpoint ledger, StreamName finite windows, RegSeqRat readback, a terminal RealUp seal, a BishopRegularCauchyCompletion handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-interval-nest-limit-carrier}, \autoref{thm:bishop-interval-nest-limit-namecert-obligations}, \autoref{thm:bishop-interval-nest-limit-convergence-route}, and \autoref{thm:bishop-interval-nest-limit-nonescape} seed the finite nested-interval induction route from displayed interval prefixes through RegSeqRat readback to the terminal Real seal and Bishop regular Cauchy completion handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close general Heine--Borel compactness, selected intersection points, quotient stream equality, countable choice, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, induction-step exposure, dyadic endpoint exactness, stream and regular readback discipline, Real-seal handoff, completion-interface non-escape, and convergence-route proofs for BEDC.Derived.BishopIntervalNestLimitUp.}
\end{closurestatus}
