\chapter{A Concrete Naming Certificate for $\CauchyRealCompletionInterfaceUp$}
\label{ch:concrete-instances-cauchy-real-completion-interface-namecert}
\origin{human}

Following Bishop and Bridges' constructive analysis, the $\CauchyRealCompletionInterfaceUp$ packet records the finite four-object boundary at which rational approximants, stream names, regular rational sequences, and the terminal Real seal can be cited together without asserting a completeness theorem. It reads the dyadic endpoint and tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite-window stream surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal seal of \autoref{ch:concrete-instances-real-namecert}, and the Bishop regular Cauchy completion carrier of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}.

The packet is an interface certificate. It names the rows that a completion-facing consumer may inspect when moving among the L10 rational, stream, regular-sequence, and Real surfaces, while excluding quotient stream equality, selected limits, countable choice, host real equality, ambient $\RealUp$ completeness, and bridge checking.

\begin{definition}[Cauchy real completion interface carrier]
\label{def:cauchy-real-completion-interface-carrier}
A $\CauchyRealCompletionInterfaceUp$ carrier is a finite $\BHist$ packet
$$
I=(D,S,R,B,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ endpoint and tolerance row used by the rational boundary, stream-window requests, regular-sequence comparisons, and Real-seal reads.
\item $S$ is the $\StreamNameUp$ finite-window row, exposing only the displayed windows that a completion consumer may replay.
\item $R$ is the $\RegSeqRatUp$ regular-rational sequence row attached to the same dyadic tolerance and stream-window data.
\item $B$ is the terminal $\RealUp$ seal row, read only after $D,S,R$ have fixed the rational, stream, and regular-sequence faces.
\item $T$ is the completion-boundary tail ledger, recording the finite handoff from dyadic tolerances through stream windows and regular rational readback to the terminal Real seal.
\item $H$ records componentwise $\hsame$ transports for the dyadic, stream, regular-sequence, Real-seal, tail-ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-boundary request through $D,S,R,B,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyRealCompletionInterfaceUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRegularCauchyCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyRealCompletionInterfaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S,R,B,T,H,C,P,N$. The carrier contains no quotient stream equality, selected limit, countable-choice selector, host real equality row, ambient $\RealUp$ completeness datum, or standard-bridge credential.
\end{definition}

\begin{theorem}[Cauchy real completion interface NameCert obligations]
\label{thm:cauchy-real-completion-interface-namecert-obligations}
For every accepted $\CauchyRealCompletionInterfaceUp$ carrier $I=(D,S,R,B,T,H,C,P,N)$, the local $\NameCert_{\CauchyRealCompletionInterfaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed DyadicRatCore endpoint and tolerance row, StreamName finite windows, RegSeqRat readback, Real seal, completion-boundary tail ledger, transport, replay, provenance, and local naming row;
\item dyadic endpoint exposure, requiring every interface read to project $D$ before inspecting stream windows, regular rational readback, or the terminal Real seal;
\item stream-window exactness, requiring $S$ to expose only finite windows tied to the displayed dyadic tolerance row;
\item regular-sequence handoff, requiring $R$ to reuse the same $D,S$ surface rather than selecting a second sequence representative;
\item Real-seal boundary, requiring every $\RealUp$ read to remain downstream of $D,S,R$ and the tail ledger $T$;
\item non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no row from which quotient stream equality, selected limits, countable choice, host real equality, ambient Real completeness, or bridge credentials can be exported.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyRealCompletionInterfaceUp.CauchyRealCompletionInterfaceTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-real-completion-interface-carrier}. The accepted packet displays exactly the dyadic endpoint and tolerance row, finite stream windows, regular-rational readback, terminal Real seal, completion-boundary tail ledger, and structural rows.

The dyadic exposure and stream-window exactness clauses are forced by the order of the carrier. A completion-boundary request first reads $D$, then obtains only the finite windows in $S$ that are tied to that displayed tolerance row.

The regular-sequence handoff is the projection to $R$. Since $R$ is stored after $D,S$, the interface has no coordinate from which a second stream representative or detached rational sequence can be selected.

The Real-seal boundary is carried by $B$ and $T$. The terminal seal is read only after the rational, stream, and regular-sequence faces have been displayed, and the tail ledger records that same handoff.

Finally, non-escape is exhausted by $H,C,P,N$. These rows transport, replay, source, and name the displayed interface only, and none contains quotient stream equality, selected limits, countable choice, host real equality, ambient Real completeness, or bridge credentials.
\end{proof}

\begin{theorem}[Cauchy real completion four-face handoff]
\label{thm:cauchy-real-completion-interface-four-face-handoff}
Let $I=(D,S,R,B,T,H,C,P,N)$ be an accepted $\CauchyRealCompletionInterfaceUp$ carrier. Every completion-facing read exported by $I$ factors through the four displayed faces
$$
D \longmapsto S \longmapsto R \longmapsto B
$$
before it can inspect the tail ledger $T$ or the structural rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with a completion-facing read of $I$. Carrier admission provides no source row before the dyadic endpoint and tolerance ledger $D$.

The read then passes to the finite-window row $S$. These windows are the only stream observations exposed by the packet, so no quotient stream equality or host stream representative can enter the route.

Next the read projects the regular-rational row $R$. This row is attached to the displayed dyadic and stream data, and it does not select a second regular sequence.

The terminal Real seal $B$ is therefore reached only after $D,S,R$. The tail ledger $T$ and structural rows $H,C,P,N$ replay the same route, so every exported completion-facing read factors through the four displayed faces in order.
\end{proof}
\leanchecked{BEDC.Derived.CauchyRealCompletionInterfaceUp.CauchyRealCompletionInterfaceUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cauchy real completion interface Real-seal route determinacy]
\label{thm:cauchy-real-completion-interface-real-seal-determinacy}
Let $I=(D,S,R,B,T,H,C,P,N)$ and $I'=(D',S',R',B',T',H',C',P',N')$ be accepted $\CauchyRealCompletionInterfaceUp$ carriers. Suppose the two packets expose componentwise matching $\DyadicRatCoreUp$ endpoint and tolerance rows, $\StreamNameUp$ finite windows, $\RegSeqRatUp$ readbacks, and terminal $\RealUp$ seal rows. Then every completion-facing consumer read of $I$ and every matching read of $I'$ reaches the same terminal Real-seal route after the four-face handoff through $D,S,R,B$ and $D',S',R',B'$. Any remaining exported comparison is exhausted by the shared $T,H,C,P,N$ rows, so there is no second seal coordinate, quotient stream equality, selected limit, countable-choice selector, host real equality, ambient completeness datum, or bridge credential along which the two reads could diverge.
\end{theorem}
\begin{proof}
Project both accepted carriers to their displayed rows. The componentwise matching assumptions identify the dyadic endpoint and tolerance rows, finite stream windows, regular-rational readbacks, and terminal Real seals as the only route data available to the two completion-facing reads.

Apply \autoref{thm:cauchy-real-completion-interface-four-face-handoff} to each carrier. Both reads must pass through the four displayed faces in order, so the matched $D,S,R,B$ and $D',S',R',B'$ rows force the same terminal Real-seal route before any tail-ledger or structural row can be inspected.

It remains to compare the residual rows. The carrier projection leaves only $T,H,C,P,N$ for completion-boundary tail data, componentwise transport, replay, provenance, and local naming. These rows replay the already matched handoff and contain no second seal coordinate, quotient stream equality, selected limit, countable-choice selector, host real equality, ambient completeness datum, or bridge credential. Hence no further route choice remains.
\end{proof}

\begin{theorem}[Cauchy real completion interface non-escape]
\label{thm:cauchy-real-completion-interface-nonescape}
For an accepted $\CauchyRealCompletionInterfaceUp$ carrier $I=(D,S,R,B,T,H,C,P,N)$, every exported comparison, replay, provenance read, or local name is exhausted by the displayed rows $D,S,R,B,T,H,C,P,N$. In particular, the packet exports no $\RealUp$ completeness theorem, quotient stream equality, selected limit, countable-choice selector, host real equality, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted packet. Its classifier compares carriers only through the displayed rows $D,S,R,B,T,H,C,P,N$.

The comparison-sensitive rows are $T,H,C,P,N$. The tail ledger records the finite handoff across $D,S,R,B$, transport is componentwise, replay follows the displayed request path, provenance names the same source chapters, and the local NameCert row names only this packet.

Since no accepted coordinate stores a quotient stream equality, selected limit, choice selector, host real equality, ambient Real-completeness datum, or bridge credential, no exported comparison or replay can use such a row. The packet therefore remains a boundary interface rather than a completeness assertion.
\end{proof}

\closureat{CauchyRealCompletionInterfaceUp}{seedStr}

\begin{closurestatus}{\CauchyRealCompletionInterfaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-real-completion-interface-carrier}, \autoref{thm:cauchy-real-completion-interface-namecert-obligations}, \autoref{thm:cauchy-real-completion-interface-four-face-handoff}, \autoref{thm:cauchy-real-completion-interface-real-seal-determinacy}, and \autoref{thm:cauchy-real-completion-interface-nonescape} seed the finite L10 interface among dyadic rational tolerances, stream windows, regular rational readback, and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close $\RealUp$ completeness, quotient stream equality, selected limits, countable choice, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic endpoint exposure, stream-window exactness, regular-sequence handoff, Real-seal boundary, four-face handoff, Real-seal route determinacy, and non-escape proofs for BEDC.Derived.CauchyRealCompletionInterfaceUp.}
  \constructivestory{A $\CauchyRealCompletionInterfaceUp$ packet is generated from a DyadicRatCore endpoint and tolerance row, StreamName finite windows, RegSeqRat readback, a terminal RealUp seal row, a completion-boundary tail ledger, componentwise hsame transports, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
