\chapter{A Concrete Naming Certificate for $\UniformBoundednessUp$}
\label{ch:concrete-instances-uniformboundedness-namecert}
\origin{human}

Following the Banach--Steinhaus theorem as presented in Bourbaki and Kreyszig, the $\UniformBoundednessUp$ packet records the finite certificate surface by which a pointwise bounded family of displayed bounded linear operators exposes a uniform bound on a displayed Baire-complete source window. It consumes the operator carrier of \autoref{ch:concrete-instances-boundedlinearoperator-namecert}, the prefix-bar completeness handoff of \autoref{ch:concrete-instances-bairemetric-namecert}, the norm rows of \autoref{ch:concrete-instances-norm-namecert}, the functional-analysis consumer face of \autoref{ch:concrete-instances-functionalanalysis-namecert}, the stream scheduler of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}. The packet is a NameCert reconstruction of the traditional theorem's visible route; it is not an unrestricted host-level Banach--Steinhaus principle.

\begin{definition}[Uniform boundedness carrier]
\label{def:uniform-boundedness-carrier}
A $\UniformBoundednessUp$ carrier is a finite $\BHist$ packet
$$
U=(F,W,B,N,R,S,Q,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is a finite family ledger of $\BoundedLinearOperatorUp$ rows $\mathsf{BanachBLOp}(X,Y_i,T_i,K_i,\Lambda_i)$ sharing the displayed source carrier $X$ and carrying target rows $Y_i$.
\item $W$ is the pointwise boundedness window. For each carried source endpoint $x$ inspected by the schedule, it records a $\NormUp$ bound row for the finite family of target reads $T_i(x)$ and the local rational budget used for that inspection.
\item $B$ is the $\BaireMetricUp$ bar and complete-metric handoff row on the source-side observation space. It records the displayed bar of windows on which pointwise boundedness is visible and the complete-metric route used to pass from local windows to a source neighbourhood.
\item $N$ is the $\NormUp$ envelope ledger. It records the source norm window, the target norm rows, and the candidate uniform operator-bound endpoint.
\item $R$ is the $\RegSeqRatUp$ readback of the rational bound budget used to compare the local pointwise windows with the single displayed uniform bound.
\item $S$ is the $\StreamNameUp$ schedule controlling which source endpoints, operator rows, norm rows, and rational comparisons may be inspected.
\item $Q$ records componentwise $\hsame$ transport for the operator family, pointwise windows, Baire handoff, norm envelope, regular-rational readback, stream schedule, continuation, provenance, and local name.
\item $H$ is the visible history row binding the operator-family reads, pointwise-boundedness witnesses, Baire bar handoff, norm-envelope rows, and readback comparisons into one $\BHist$ packet.
\item $C$ records displayed $\Cont$ replay from a requested family-bound read through $F,W,B,N,R,S,Q,H,P,L$.
\item $P$ is the $\Pkg$ provenance over $\UniformBoundednessUp$, $\BoundedLinearOperatorUp$, $\BaireMetricUp$, $\NormUp$, $\FunctionalAnalysisUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\UniformBoundednessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the listed rows. It has no coordinate for host function extensionality, choice-selected uniform constants, quotient operator equality, a hidden operator space, or the unrestricted classical Banach--Steinhaus theorem.
\end{definition}
\leanchecked{BEDC.Derived.UniformBoundednessUp.UniformBoundednessUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Uniform boundedness NameCert obligations]
\label{thm:uniform-boundedness-namecert-obligations}
For every accepted $\UniformBoundednessUp$ carrier
$$
U=(F,W,B,N,R,S,Q,H,C,P,L),
$$
the local $\NameCert_{\UniformBoundednessUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the shared-source family of $\BoundedLinearOperatorUp$ rows, pointwise boundedness windows, Baire bar handoff, norm envelope, regular-rational readback, stream schedule, transport, history, replay, provenance, and local naming;
\item family coherence, requiring every operator row in $F$ to share the displayed source carrier and to expose its endpoint action and norm bound through \autoref{def:bounded-linear-operator-carrier};
\item pointwise boundedness admission, requiring $W$ to give only scheduled source endpoints and scheduled operator reads;
\item Baire handoff compatibility, requiring $B$ to be the only route from pointwise windows to a source neighbourhood;
\item norm-envelope exactness, requiring $N$ and $R$ to display the same rational budget and the same uniform operator-bound endpoint;
\item ledger refusal, excluding host function extensionality, choice-selected uniform constants, quotient operator equality, hidden operator-space completion, and an unrestricted classical Banach--Steinhaus theorem.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.UniformBoundednessUp.UniformBoundednessPacket\_namecert\_obligations}
\leanvariant{BEDC.Derived.UniformBoundednessUp.UniformBoundednessTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-boundedness-carrier}. The tuple lists the finite operator family, pointwise boundedness window, Baire handoff, norm envelope, regular-rational readback, stream schedule, transport, history, replay, provenance, and local name.

Family coherence is read from $F$. Each member is a $\BoundedLinearOperatorUp$ carrier over the same displayed source, so the endpoint actions, bound endpoints, and operator ledgers are exactly the rows admitted by \autoref{thm:bounded-linear-operator-namecert-obligations}.

Pointwise boundedness is local to $W$ and $S$. The schedule chooses the finite source reads and the finite operator reads, while $W$ records only the corresponding target-norm comparisons and rational budgets.

The passage from local pointwise windows to a source neighbourhood is routed through $B$. By \autoref{thm:bairemetric-namecert-obligations}, the handoff may inspect only displayed prefix windows, bar data, metric rows, transport, replay, provenance, and local naming.

Finally $N$ and $R$ bind the visible norm envelope to the regular-rational readback. Since the classifier sees only $F,W,B,N,R,S,Q,H,C,P,L$, none of the excluded host or quotient principles can be exported as a NameCert obligation.
\end{proof}

\begin{theorem}[Uniform boundedness Baire handoff]
\label{thm:uniform-boundedness-baire-handoff}
Every accepted $\UniformBoundednessUp$ carrier factors the passage from pointwise boundedness to a uniform source-window bound through the displayed route
$$
\StreamNameUp,\BaireMetricUp,\RegSeqRatUp,\NormUp .
$$
The stream schedule first names finite source and operator reads, the Baire row supplies the bar and complete-metric handoff, the regular-rational row reads the finite bound budget, and the norm row records the source and target bound comparisons. No completed host space or countable-choice selector is introduced by the route.
\end{theorem}
\begin{proof}
Read an accepted carrier as $U=(F,W,B,N,R,S,Q,H,C,P,L)$. A pointwise boundedness read must begin with $S$, because $W$ has no unscheduled source endpoint or unscheduled operator coordinate.

The Baire step is then forced through $B$. It is the only carrier coordinate naming a bar and complete-metric handoff, and \autoref{thm:bairemetric-ultrametric-prefix-route} confines such handoffs to displayed prefix, schedule, radius, metric, and ultrametric rows.

The rational and norm comparisons are downstream of that handoff. The row $R$ reads the regular rational budget attached to the selected window, and $N$ records the matching norm envelope and uniform-bound endpoint.

Thus the source-window bound is obtained only by replaying $S,B,R,N$ with the structural rows $Q,H,C,P,L$. The carrier contains no coordinate for a completed ambient host space or a countable-choice selector, so neither can be read from the handoff.
\end{proof}

\begin{theorem}[Uniform boundedness bounded-operator envelope]
\label{thm:uniform-boundedness-bounded-operator-envelope}
Let $U$ be an accepted $\UniformBoundednessUp$ carrier. Every uniform operator-bound conclusion exported by $U$ reads each family member through a $\BoundedLinearOperatorUp$ carrier row and reads the common bound through $\NormUp$ and $\RegSeqRatUp$ rows. In particular, the functional-analysis consumer face receives only the displayed operator ledgers, pointwise boundedness windows, Baire handoff, rational readback, and norm-envelope rows named in \autoref{def:uniform-boundedness-carrier}.
\end{theorem}
\begin{proof}
Open the family row $F$. By construction its entries are $\BoundedLinearOperatorUp$ packets sharing the source carrier, so \autoref{thm:bounded-linear-operator-nonescape-boundary} makes the endpoint action, bound endpoint, linearity ledger, norm ledger, history, replay, provenance, and local naming the only readable operator data.

The common envelope is not an additional operator-space object. It is the row $N$ together with the rational readback $R$, so the comparison between individual operator bounds and the displayed uniform bound is carried by $\NormUp$ and $\RegSeqRatUp$ evidence.

The $\FunctionalAnalysisUp$ consumer face therefore receives the same bounded-operator rows and the same norm-bound ledgers described in \autoref{thm:functionalanalysis-operator-norm-stability-obligation}. The uniform boundedness packet adds only the scheduled pointwise windows and the Baire handoff that justify reading one envelope from the finite family ledger.
\end{proof}

\begin{theorem}[Uniform boundedness public boundary]
\label{thm:uniform-boundedness-public-boundary}
Every accepted $\UniformBoundednessUp$ consumer factors through the displayed route
$$
\BoundedLinearOperatorUp,\BaireMetricUp,\NormUp,\FunctionalAnalysisUp,\StreamNameUp,\RegSeqRatUp,\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
The public packet explicitly excludes host function extensionality, choice-selected uniform constants, quotient operator equality, hidden completion of an operator space, and an unrestricted classical Banach--Steinhaus theorem.
\end{theorem}
\begin{proof}
Let a consumer read an accepted carrier. By \autoref{def:uniform-boundedness-carrier}, the only visible coordinates are the operator family, pointwise window, Baire handoff, norm envelope, rational readback, stream schedule, componentwise transport, history, replay, provenance, and local name.

The operator data are confined by \autoref{thm:uniform-boundedness-bounded-operator-envelope}. The Baire passage is confined by \autoref{thm:uniform-boundedness-baire-handoff}, and the finite NameCert obligation surface is exactly the one listed in \autoref{thm:uniform-boundedness-namecert-obligations}.

Combining these three readings gives the displayed public route and no other route. Since no carrier coordinate stores a host function-extensionality principle, a selected uniform constant, quotient equality of operators, hidden operator-space completion, or the full classical theorem, none of those objects can be exported by a public $\UniformBoundednessUp$ consumer.
\end{proof}

\falsifiablePrediction{Every accepted $\UniformBoundednessUp$ uniform-bound read factors through one finite family of $\BoundedLinearOperatorUp$ rows, one pointwise boundedness window, one $\BaireMetricUp$ bar handoff, one $\NormUp$ envelope, one $\RegSeqRatUp$ rational readback, one $\StreamNameUp$ schedule, componentwise $\hsame$ transport, one $\BHist$ ledger, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{boundedlinearoperator, bairemetric, norm, functionalanalysis, streamname, regseqrat: $\UniformBoundednessUp$ is not bijective to any listed sibling because it jointly carries a shared-source operator family, pointwise boundedness windows, a Baire bar handoff, a norm envelope, regular-rational readback, scheduling, transport, replay, provenance, and local naming.}

\closureat{UniformBoundednessUp}{seedStr}

\begin{closurestatus}{\UniformBoundednessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-boundedness-carrier}, \autoref{thm:uniform-boundedness-namecert-obligations}, \autoref{thm:uniform-boundedness-baire-handoff}, \autoref{thm:uniform-boundedness-bounded-operator-envelope}, and \autoref{thm:uniform-boundedness-public-boundary} seed the finite Banach--Steinhaus NameCert surface over displayed bounded-operator families, Baire handoffs, norm envelopes, scheduled pointwise windows, and regular-rational readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host function extensionality, choice-selected uniform constants, quotient operator equality, hidden completion of an operator space, an unrestricted classical Banach--Steinhaus theorem, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, family coherence, pointwise boundedness admission, Baire handoff compatibility, norm-envelope exactness, ledger refusal, and public-boundary nonescape for BEDC.Derived.UniformBoundednessUp.}
  \constructivestory{A $\UniformBoundednessUp$ packet is generated from a finite shared-source family of $\BoundedLinearOperatorUp$ rows, scheduled pointwise boundedness windows, a $\BaireMetricUp$ bar and complete-metric handoff, $\NormUp$ envelope rows, $\RegSeqRatUp$ rational readback, $\StreamNameUp$ scheduling, componentwise transport, a visible history ledger, replay, provenance, and a local NameCert row.}
\end{closurestatus}
