\chapter{A Concrete Naming Certificate for $\CauchyPrecompletionUp$}
\label{ch:concrete-instances-cauchy-precompletion-namecert}
\origin{human}

Following Bishop and Bridges and Kelley constructive completion, the $\CauchyPrecompletionUp$ packet collects displayed regular Cauchy names before quotient, separated completion, or ambient completeness is read. It sits after the dyadic rational endpoint and tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, while remaining upstream of the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, the completion-embedding interface of \autoref{ch:concrete-instances-completionembedding-namecert}, the separated completion boundary of \autoref{ch:concrete-instances-separatedcompletion-namecert}, and the constructive metric completion surface of \autoref{ch:concrete-instances-constructive-metric-completion-namecert}.

The packet is a pre-separated collection boundary. It names the finite rows a completion consumer may inspect when assembling regular Cauchy data, but it does not quotient names, select representatives, invoke countable choice, identify host reals, assert ambient $\RealUp$ completeness, close compactness by open covers, or provide a standard bridge.

\begin{definition}[CauchyPrecompletion carrier]
\label{def:cauchy-precompletion-carrier}
A $\CauchyPrecompletionUp$ carrier is a finite $\BHist$ packet
$$
Q=(W,R,D,S,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the source window family, listing the finite $\StreamNameUp$ requests whose displayed entries are admitted before any quotient or separated completion step.
\item $R$ is the regular Cauchy readback row, carrying the $\RegSeqRatUp$ regular rational sequence read from those source windows.
\item $D$ is the dyadic tolerance ledger, recording the $\DyadicRatCoreUp$ endpoints and tolerance budgets used by $W$ and $R$.
\item $S$ is the finite stream-observation row, exposing only the displayed stream entries attached to $W,D,R$.
\item $E$ is the completion-embedding handoff row, naming the downstream $\CompletionEmbeddingUp$, $\SeparatedCompletionUp$, and $\ConstructiveMetricCompletionUp$ consumers without giving them a quotient, a selected representative, or a completeness proof.
\item $H$ records componentwise $\hsame$ transport for the source-window, regular-readback, dyadic-ledger, stream-observation, handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a precompletion request through $W,R,D,S,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyPrecompletionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompletionEmbeddingUp$, $\SeparatedCompletionUp$, $\ConstructiveMetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyPrecompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,R,D,S,E,H,C,P,N$. The carrier contains no quotient completion row, selected representative, countable-choice schedule, host equality, ambient $\RealUp$ completeness datum, open-cover compactness datum, Lean verification credential, or standard bridge.
\end{definition}
\leanchecked{BEDC.Derived.CauchyPrecompletionUp.TasteGate.CauchyPrecompletionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyPrecompletion NameCert obligations]
\label{thm:cauchy-precompletion-namecert-obligations}
For every accepted $\CauchyPrecompletionUp$ carrier $Q=(W,R,D,S,E,H,C,P,N)$, the local $\NameCert_{\CauchyPrecompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source window family, regular Cauchy readback, dyadic tolerance ledger, finite stream observations, completion-embedding handoff, transport, replay, provenance, and local naming row;
\item source-window locality, requiring every precompletion request to read only the displayed finite windows in $W$ before it can inspect the regular Cauchy readback;
\item regular-readback attachment, requiring $R$ to be tied to the same source windows and dyadic ledger rather than to a second stream name or host representative;
\item dyadic-tolerance exactness, requiring $D$ to provide the endpoint and tolerance budget used by both the source windows and the readback row;
\item finite-observation exactness, requiring $S$ to expose only displayed stream observations attached to $W,R,D$;
\item downstream handoff, requiring $E$ to name only completion-embedding, separated-completion, and constructive-metric-completion consumers without exporting their quotient, representative, completeness, compactness, or bridge data;
\item non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no row outside $W,R,D,S,E,H,C,P,N$.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-precompletion-carrier}. The accepted packet displays exactly the source window family, regular Cauchy readback, dyadic tolerance ledger, finite stream observations, completion-embedding handoff, and structural rows.

Source-window locality and regular-readback attachment are forced by the order of the carrier. A precompletion request first reads $W$, then obtains the regular rational readback $R$ attached to the same windows rather than to a second stream name or host representative.

Dyadic-tolerance and finite-observation exactness are supplied by $D$ and $S$. The dyadic ledger records the endpoint and tolerance budget for both the source windows and the readback row, while $S$ exposes only the displayed observations tied to that same data.

The downstream handoff is the row $E$. It names completion-embedding, separated-completion, and constructive-metric-completion consumers as later readers, but it has no coordinate from which to export a quotient completion, selected representative, completeness theorem, open-cover compactness datum, or bridge credential.

Finally, non-escape is exhausted by $H,C,P,N$. These rows transport, replay, source, and name the displayed precompletion packet only, so no local obligation is stored outside $W,R,D,S,E,H,C,P,N$.
\end{proof}

\begin{theorem}[CauchyPrecompletion regular handoff]
\label{thm:cauchy-precompletion-regular-handoff}
Every completion-facing read of an accepted $\CauchyPrecompletionUp$ carrier $Q=(W,R,D,S,E,H,C,P,N)$ factors through the displayed regular Cauchy route
$$
W,D,S \longmapsto R \longmapsto E
$$
before it can be replayed, transported, sourced, or locally named. Consequently the packet hands regular Cauchy names to completion interfaces without quotienting them, selecting representatives, invoking countable choice, or asserting ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $Q=(W,R,D,S,E,H,C,P,N)$. The source window family $W$ is the only row from which a completion-facing request may obtain stream entries.

The read then exposes the shared dyadic tolerance ledger $D$ and the finite observation row $S$. These rows fix the endpoint budget and the displayed stream observations before any regular readback is used.

The regular Cauchy readback $R$ is therefore reached through $W,D,S$. Since $R$ is attached to the same displayed data, the packet has no coordinate for a second stream name, quotient class, selected representative, choice schedule, or host real equality.

The handoff row $E$ names downstream completion consumers only after the regular route has been displayed. Transport, replay, provenance, and local naming preserve that same route, so the handoff remains a pre-separated regular Cauchy boundary rather than an ambient completeness assertion.
\end{proof}

\begin{theorem}[CauchyPrecompletion nonescape]
\label{thm:cauchy-precompletion-nonescape}
Every exported comparison, replay, provenance read, or local name of an accepted $\CauchyPrecompletionUp$ carrier $Q=(W,R,D,S,E,H,C,P,N)$ is exhausted by the displayed rows $W,R,D,S,E,H,C,P,N$. In particular, the packet exports no quotient completion, selected representative, countable-choice selector, host equality, ambient $\RealUp$ completeness theorem, open-cover compactness principle, Lean verification marker, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted packet. Its classifier compares carriers only through the tuple $W,R,D,S,E,H,C,P,N$ named in \autoref{def:cauchy-precompletion-carrier}.

The analytic rows are $W,R,D,S,E$. They display the source windows, regular readback, dyadic tolerance ledger, finite observations, and downstream handoff surface, without adding a quotient row or an ambient completeness coordinate.

The structural rows do not enlarge the boundary. Componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row only preserve, replay, source, and name the same displayed packet.

Since no excluded object appears as a coordinate or replay target, no exported comparison, provenance read, or local name can escape to quotient completion, selected representatives, countable choice, host equality, ambient $\RealUp$ completeness, open-cover compactness, Lean verification, or bridge checking.
\end{proof}

\closureat{CauchyPrecompletionUp}{seedStr}

\begin{closurestatus}{\CauchyPrecompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-precompletion-carrier}, \autoref{thm:cauchy-precompletion-namecert-obligations}, \autoref{thm:cauchy-precompletion-regular-handoff}, and \autoref{thm:cauchy-precompletion-nonescape} seed the finite pre-separated regular Cauchy collection boundary over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CompletionEmbeddingUp$, $\SeparatedCompletionUp$, and $\ConstructiveMetricCompletionUp$ rows.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CauchyPrecompletionUp.TasteGate.CauchyPrecompletionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, countable choice, host equality, ambient $\RealUp$ completeness, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-window locality, regular-readback attachment, dyadic-tolerance exactness, finite-observation exactness, completion-embedding handoff, regular handoff, and non-escape proofs for BEDC.Derived.CauchyPrecompletionUp.}
  \constructivestory{A $\CauchyPrecompletionUp$ packet is generated from a source window family, regular Cauchy readback, DyadicRatCore tolerance ledger, finite StreamName observations, completion-embedding handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
