\chapter{A Concrete Naming Certificate for $\ObserverBudgetSupportUp$}
\label{ch:concrete-instances-observer-budget-support-namecert}
\origin{ai}

The $\ObserverBudgetSupportUp$ packet realizes observer-local support readings from \autoref{ch:visions-consciousness-universe-observer-in-bedc} as one finite support-and-budget carrier. It sits after the observer-coordinate surface of \autoref{ch:concrete-instances-observer-coordinate-frame-namecert}, the selected observer budget of \autoref{ch:concrete-instances-observer-filter-budget-selector-namecert}, the finite support surface of \autoref{ch:concrete-instances-finitesupport-namecert}, and the cross-Hist causal surface of \autoref{ch:concrete-instances-crosshistcausal-namecert}. Its role is to bind the local observer frame, finite support ledger, causal witness rows, and budget cap before any observer-local consumer reads a finite ledger slice as a coherent support surface.

\begin{definition}[Observer-budget support carrier]
\label{def:observer-budget-support-carrier}
An $\ObserverBudgetSupportUp$ carrier is a finite $\BHist$ packet
$$
O=(F,S,X,B,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\ObserverCoordinateFrameUp$ row naming the observer-local coordinate surface, not a global frame;
\item $S$ is the $\FiniteSupportUp$ row listing the finite ledger entries visible to the observer;
\item $X$ is the $\CrossHistCausalUp$ row recording the witnessed cross-Hist dependence used by the reading;
\item $B$ is the $\ObserverFilterBudgetSelectorUp$ row bounding the selected observation budget;
\item $T$ is the support-transport row tying $F,S,X,B$ into one observer-local route;
\item $H$ records componentwise $\hsame$ transport for the frame, support, causal, budget, transport, provenance, and naming rows;
\item $C$ records displayed $\Cont$ replay of the observer-coordinate read, support ledger read, cross-Hist causal read, budget read, and support transport;
\item $P$ is the $\Pkg$ provenance over $\ObserverCoordinateFrameUp$, $\ObserverFilterBudgetSelectorUp$, $\FiniteSupportUp$, $\CrossHistCausalUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ObserverBudgetSupportUp}$ row.
\end{enumerate}
The carrier has no coordinate for a global observer frame, infinite support set, unbounded observation budget, unwitnessed cross-Hist relation, host spacetime object, quotient history equality, or detached support route.
\end{definition}
\leanchecked{BEDC.Derived.ObserverBudgetSupportUp.ObserverBudgetSupportTasteGate\_carrier\_recognition}

\begin{theorem}[Observer-budget support NameCert obligations]
\label{thm:observer-budget-support-namecert-obligations}
For the carrier of \autoref{def:observer-budget-support-carrier}, the local $\NameCert_{\ObserverBudgetSupportUp}$ surface consists of five rows:
\begin{enumerate}
\item carrier admission for $O=(F,S,X,B,T,H,C,P,N)$;
\item observer-coordinate admission through $F$;
\item finite support and selected-budget admission through $S$ and $B$;
\item cross-Hist causal visibility through $X$ together with support transport through $T$;
\item componentwise $\hsame$ transport, displayed replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
No observer-local reading through this packet can bypass one of these rows.
\end{theorem}
\leanchecked{BEDC.Derived.ObserverBudgetSupportUp.ObserverBudgetSupportNameCert\_obligations}
\begin{proof}
Project the carrier. The packet contains exactly the frame row $F$, support row $S$, causal row $X$, budget row $B$, transport row $T$, and structural rows $H,C,P,N$.

Read the sibling surfaces. The observer-coordinate row supplies the local frame, the finite-support row supplies the displayed ledger support, the cross-Hist causal row supplies witnessed dependence, and the observer-budget row supplies the selected finite budget.

Finally inspect $T,H,C,P,N$. The support-transport row ties the four sibling rows into one route, while the structural rows preserve, replay, source, and name that route. Since the carrier contains no further coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Observer-budget support nontrivial boundary]
\label{thm:observer-budget-support-nontrivial-boundary}
An accepted $\ObserverBudgetSupportUp$ packet is nontrivial exactly as a joint observer-local support-and-budget carrier: removing any one of $F,S,X,B,T$ destroys one of observer-coordinate locality, finite support visibility, witnessed cross-Hist dependence, selected-budget boundedness, or the route tying them together. The packet is therefore not a renaming of any single sibling surface.
\end{theorem}
\begin{proof}
Start from the carrier in \autoref{def:observer-budget-support-carrier}. The five content rows $F,S,X,B,T$ play distinct roles in the accepted packet.

The row $F$ supplies observer-coordinate locality; without it the packet has no local frame boundary. The row $S$ supplies finite support; without it the reading has no finite ledger support. The row $X$ supplies witnessed cross-Hist dependence; without it the route has no causal surface. The row $B$ supplies the selected observation budget; without it the reading is unbounded. The row $T$ ties those four rows into one route; without it the packet is only a list of sibling citations.

Thus the boundary is nontrivial at the carrier level. No projection to a single sibling can be inverted without recreating omitted rows.
\end{proof}

\begin{theorem}[Observer-budget support field faithfulness]
\label{thm:observer-budget-support-field-faithfulness}
Every field-faithful observer-local consumer of an accepted $\ObserverBudgetSupportUp$ packet must preserve the full tuple
$$
F,S,X,B,T,H,C,P,N.
$$
In particular, it cannot keep the observer-coordinate row while dropping finite support, keep finite support while dropping the budget, keep the causal row while dropping transport, or read provenance and local naming as detached evidence.
\end{theorem}
\begin{proof}
Use the NameCert obligations of \autoref{thm:observer-budget-support-namecert-obligations}. Each public read is assigned to one of the displayed rows $F,S,X,B,T,H,C,P,N$.

Field faithfulness is therefore rowwise. Dropping $S$ erases the support ledger, dropping $B$ erases the selected budget, dropping $X$ erases the witnessed cross-Hist dependence, and dropping $T$ disconnects the sibling rows from the observer-local route.

The structural rows are also part of the same carrier. Transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ cannot be read as detached evidence because the carrier has no coordinate outside the displayed tuple. Hence a faithful consumer preserves all nine rows.
\end{proof}

\begin{theorem}[Observer-budget support route totality]
\label{thm:observer-budget-support-route-totality}
Every accepted observer-local read of an $\ObserverBudgetSupportUp$ packet routes through the finite tuple
$$
F,S,X,B,T,H,C,P,N.
$$
The route may read the observer-coordinate row, finite support row, cross-Hist causal row, selected budget row, support transport row, componentwise $\hsame$ row, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, but it has no coordinate for a global observer frame, infinite support set, unbounded budget, host spacetime object, or unwitnessed cross-Hist relation.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:observer-budget-support-carrier}. It lists $F,S,X,B,T,H,C,P,N$ as the complete support-and-budget packet.

Apply the NameCert obligations of \autoref{thm:observer-budget-support-namecert-obligations}. They force observer-coordinate admission through $F$, finite support through $S$, selected budget through $B$, causal visibility through $X$, and support transport through $T$ before the structural rows can be consumed.

Finally use the nontrivial boundary and field-faithfulness rows from \autoref{thm:observer-budget-support-nontrivial-boundary} and \autoref{thm:observer-budget-support-field-faithfulness}. Since no faithful consumer can drop any content row, every accepted route is total on the displayed tuple.
\end{proof}
\leanchecked{BEDC.Derived.ObserverBudgetSupportUp.ObserverBudgetSupportRouteTotality}

\begin{theorem}[Observer-budget support ledger exactness]
\label{thm:observer-budget-support-ledger-exactness}
In an accepted $\ObserverBudgetSupportUp$ packet, finite support, selected budget, cross-Hist causal evidence, and support transport are exact ledger rows rather than detached evidence. A consumer reads $S$, $B$, $X$, and $T$ only as rows of the same carrier
$$
F,S,X,B,T,H,C,P,N.
$$
\end{theorem}
\begin{proof}
Project the carrier. The finite support row $S$, selected budget row $B$, causal row $X$, and transport row $T$ appear in the same packet as the observer-coordinate and structural rows.

Use the NameCert obligations to read these rows together. The local certificate does not allow the support row to detach from the budget, the causal evidence to detach from transport, or the provenance and naming rows to certify a different object.

Now apply the nontrivial boundary and field-faithfulness theorems. Removing $S$, $B$, $X$, or $T$ destroys the intended observer-local support-and-budget packet, so these rows are exact ledger content and not replaceable external evidence.
\end{proof}

\begin{theorem}[Observer-budget support public readback]
\label{thm:observer-budget-support-public-readback}
Every public readback of an accepted $\ObserverBudgetSupportUp$ packet consumes the observer-coordinate row $F$, finite support row $S$, cross-Hist causal row $X$, selected budget row $B$, and support route row $T$ together with the structural rows $H,C,P,N$. Thus public readback cannot expose support, causal evidence, budget, or route as independent host data.
\end{theorem}
\begin{proof}
Start with route totality from \autoref{thm:observer-budget-support-route-totality}. Any accepted observer-local read already passes through $F,S,X,B,T,H,C,P,N$.

Add ledger exactness from \autoref{thm:observer-budget-support-ledger-exactness}. The support, budget, causal, and route rows are not detachable evidence; they are ledger rows of the same accepted carrier.

Finally apply field faithfulness from \autoref{thm:observer-budget-support-field-faithfulness}. A public consumer that drops any of $F,S,X,B,T$ no longer preserves the accepted packet, so every public readback consumes the full observer-coordinate, support, causal, budget, and route surface together.
\end{proof}

\begin{theorem}[Observer-budget support obligation-closure package]
\label{thm:observer-budget-support-obligation-closure-package}
The carrier, NameCert obligations, nontrivial boundary, field-faithfulness, route-totality, ledger-exactness, and public-readback rows assemble the obligation-closure surface for $\ObserverBudgetSupportUp$. Every accepted observer-local support reading is bound to
$$
F,S,X,B,T,H,C,P,N
$$
through the displayed $\BHist$ carrier, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\ObserverBudgetSupportUp}$ row.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:observer-budget-support-carrier} and the NameCert obligations of \autoref{thm:observer-budget-support-namecert-obligations}. They display the observer-coordinate, finite-support, cross-Hist causal, selected-budget, support-transport, and structural rows.

Use the nontrivial boundary and field-faithfulness theorems, \autoref{thm:observer-budget-support-nontrivial-boundary} and \autoref{thm:observer-budget-support-field-faithfulness}. Together they show that no accepted consumer can collapse the packet to one sibling row or drop any displayed field.

Finally apply route totality, ledger exactness, and public readback from \autoref{thm:observer-budget-support-route-totality}, \autoref{thm:observer-budget-support-ledger-exactness}, and \autoref{thm:observer-budget-support-public-readback}. These results bind observer-local support, selected budget, causal evidence, transport, replay, provenance, and local naming into one obligation surface.
\end{proof}

\begin{theorem}[Observer-budget support bridge surface]
\label{thm:observer-budget-support-bridge-surface}
Every bridge-facing observer-local support export of an accepted $\ObserverBudgetSupportUp$ packet factors through the finite tuple
$$
F,\quad S,\quad X,\quad B,\quad T,\quad H,\quad C,\quad P,\quad N.
$$
The observer-coordinate row $F$, finite-support row $S$, cross-$\BHist$ causal row $X$, selected budget row $B$, support-transport row $T$, componentwise $\hsame$ row $H$, displayed $\Cont$ replay row $C$, $\Pkg$ provenance row $P$, and local $\NameCert_{\ObserverBudgetSupportUp}$ row $N$ are preserved as one bridge surface. No bridge-facing export may replace them by global observer frames, infinite support, unbounded budgets, detached host spacetime data, quotient history equality, or unwitnessed cross-$\BHist$ dependence.
\end{theorem}
\begin{proof}
First read the local certificate. The carrier and NameCert obligations, \autoref{def:observer-budget-support-carrier} and \autoref{thm:observer-budget-support-namecert-obligations}, display exactly the observer-coordinate, finite-support, causal, budget, transport, replay, provenance, and naming rows.

Next pass through the public surface. Public readback, \autoref{thm:observer-budget-support-public-readback}, requires every accepted observer-local read to consume $F,S,X,B,T,H,C,P,N$ together rather than as detachable host data.

Finally use the obligation package and ledger exactness. Theorem~\ref{thm:observer-budget-support-obligation-closure-package} assembles the same finite tuple as the chapter surface, and Theorem~\ref{thm:observer-budget-support-ledger-exactness} rules out replacing support, budget, causal evidence, or route transport by external witnesses. Thus a bridge-facing export preserves precisely the displayed tuple, with no additional coordinate for the excluded objects.
\end{proof}

The later Lean \texttt{TasteGate.lean} development for $\ObserverBudgetSupportUp$ will need explicit $\Nontrivial\ \ObserverBudgetSupportUp$ and $\FieldFaithful\ \ObserverBudgetSupportUp$ instances. These instances must preserve the observer-coordinate row, finite-support row, cross-Hist causal row, selected-budget row, support-transport row, componentwise transport, displayed replay, provenance, and local naming row.

\falsifiablePrediction{If an accepted observer-local reading keeps the observer-coordinate row while replacing finite support, selected budget, cross-Hist causal evidence, or support transport by detached host data, it refutes the $\ObserverBudgetSupportUp$ classifier.}

\independenceWitness{observercoordinateframe, observerfilterbudgetselector, finitesupport, crosshistcausal, observationbudgetlimiter: none is bijective to $\ObserverBudgetSupportUp$ because the carrier binds observer-local frame, finite support, cross-Hist causal evidence, selected budget, route transport, structural replay, provenance, and local NameCert rows in one packet.}

\closureat{ObserverBudgetSupportUp}{scopedStr}[BEDC.Derived.ObserverBudgetSupportUp.taste\_gate]
\closureat{ObserverBudgetSupportUp}{bridgedStr}[BEDC.Derived.ObserverBudgetSupportUp.taste\_gate]
\closureat{ObserverBudgetSupportUp}{matureStr}[BEDC.Derived.ObserverBudgetSupportUp.taste\_gate]

\begin{closurestatus}{\ObserverBudgetSupportUp}
  \constructivestory{An $\ObserverBudgetSupportUp$ packet is generated from observer-coordinate, finite-support, cross-Hist causal, selected-budget, support-transport, componentwise hsame, displayed Cont, Pkg provenance, and local NameCert rows.}
  \leanchecked{BEDC.Derived.ObserverBudgetSupportUp.taste\_gate}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:observer-budget-support-carrier}, \autoref{thm:observer-budget-support-namecert-obligations}, \autoref{thm:observer-budget-support-nontrivial-boundary}, \autoref{thm:observer-budget-support-field-faithfulness}, \autoref{thm:observer-budget-support-public-readback}, \autoref{thm:observer-budget-support-obligation-closure-package}, and \autoref{thm:observer-budget-support-bridge-surface} bind the observer-local support obligations, public readback row, obligation-closure package, and bridge-facing export surface to $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\ObserverCoordinateFrameUp$, $\FiniteSupportUp$, $\ObserverFilterBudgetSelectorUp$, $\CrossHistCausalUp$, and the support-transport row.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ObserverBudgetSupportUp.taste\_gate}
  \bridgestatus{paperBridge}
  \origin{ai}
  \notclaimed{This chapter does not close bridge checking, global observer frames, infinite support, unbounded budgets, host spacetime objects, quotient history equality, or unwitnessed cross-Hist dependence.}
  \upgradepath{Bridge checking remains a separate verification-axis obligation for the observer-local support export surface.}
\end{closurestatus}
