\chapter{A Concrete Naming Certificate for $\RealOscillationUp$}
\label{ch:concrete-instances-real-oscillation-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealOscillationUp$ packet records the finite oscillation interface by which a real-facing consumer reads tail variation, interval clamping, and squeeze enclosure before it treats a displayed name as Real or Completion data. It refines the tail ledger of \autoref{ch:concrete-instances-cauchyoscillation-namecert}, the interval route of \autoref{ch:concrete-instances-real-clamping-namecert}, and the envelope route of \autoref{ch:concrete-instances-regular-cauchy-squeeze-namecert}. Its numerical rows are grounded in the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet is therefore a finite L10 interface for oscillation arguments, not an assertion of ambient Real completeness or host equality.

\begin{definition}[Real oscillation carrier]
\label{def:real-oscillation-carrier}
A $\RealOscillationUp$ carrier is a finite $\BHist$ packet
$$
Q_{\mathrm{osc}}=(X,O,C,S,D,W,R,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\RealUp$ seal whose oscillation-facing reads are being routed.
\item $O$ is the $\CauchyOscillationUp$ row exposing the finite tail-variation ledger.
\item $C$ is the $\RealClampingUp$ interval row recording the clamped bounded-window route.
\item $S$ is the $\RegularCauchySqueezeUp$ envelope row recording the lower, middle, and upper regular Cauchy squeeze data.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row supplying the dyadic radius and endpoint slack consumed by $O,C,S$.
\item $W$ is the $\StreamNameUp$ window row opened at the precision named by $D$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from $X,O,C,S,D,W$ before any Real or Completion-facing oscillation conclusion is exposed.
\item $H$ records componentwise $\hsame$ transport for the Real seal, oscillation ledger, clamp interval, squeeze envelope, dyadic tolerance, window, readback, replay, provenance, and local naming rows.
\item $T$ records displayed $\Cont$ replay from each Real or Completion-facing oscillation request through $O,C,S,D,W,R,H,P,N$ before $X$ is consumed as a terminal seal.
\item $P$ is the $\Pkg$ provenance over $\RealOscillationUp$, $\RealUp$, $\CauchyOscillationUp$, $\RealClampingUp$, $\RegularCauchySqueezeUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealOscillationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,O,C,S,D,W,R,H,T,P,N$ and the displayed routes among those rows. It has no coordinate for ambient $\RealUp$ completeness, quotient stream equality, host trichotomy, selected limits, countable choice, Lean verification, or bridge checking.
\end{definition}
\leandef{BEDC.Derived.RealOscillationUp.RealOscillationCarrier}

\begin{theorem}[Real oscillation NameCert obligations]
\label{thm:real-oscillation-namecert-obligations}
For every accepted $\RealOscillationUp$ carrier
$$
Q_{\mathrm{osc}}=(X,O,C,S,D,W,R,H,T,P,N),
$$
the local $\NameCert_{\RealOscillationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the Real seal, CauchyOscillation ledger, RealClamping interval, RegularCauchySqueeze envelope, dyadic tolerance, StreamName window, RegSeqRat readback, transport, replay, provenance, and local naming rows;
\item oscillation-ledger exposure, requiring $O$ to be displayed before any Real or Completion-facing oscillation read can consume the seal $X$;
\item clamp interval exposure, requiring $C,D,W,R$ to display the bounded interval route used by the oscillation packet;
\item squeeze-envelope compatibility, requiring $S$ to consume the same tolerance, window, and regular rational readback route as the oscillation and clamp rows;
\item ledger nonescape, requiring $H,T,P,N$ to export no ambient Real completeness, quotient stream equality, host trichotomy, selected limit, countable-choice schedule, Lean verification, standard bridge credential, or row outside $Q_{\mathrm{osc}}$.
\end{enumerate}
No Real oscillation obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.RealOscillationUp.RealOscillationTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:real-oscillation-carrier}. The accepted packet displays exactly the Real seal, oscillation ledger, clamp interval, squeeze envelope, tolerance, finite window, readback, transport, replay, provenance, and local naming rows.

Oscillation-ledger exposure is forced by the row $O$. A consumer cannot inspect the terminal seal $X$ as oscillation evidence before the CauchyOscillation ledger has displayed the tail-variation data attached to the same packet.

The clamp and squeeze obligations are the two bounded routes around that ledger. The clamp row $C$ is read through $D,W,R$, while the squeeze row $S$ uses the same tolerance, window, and readback route to align its envelope with the displayed oscillation ledger.

The structural rows $H,T,P,N$ transport, replay, source, and name the same finite packet. Since the carrier inventory omits ambient completeness, quotient stream equality, host trichotomy, selected limits, countable choice, Lean verification, bridge credentials, and external rows, the listed obligations exhaust the local certificate surface.
\end{proof}
\leanchecked{BEDC.Derived.RealOscillationUp.RealOscillationUpTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Real oscillation clamped-window factorization]
\label{thm:real-oscillation-clamped-window-factorization}
Let
$$
Q_{\mathrm{osc}}=(X,O,C,S,D,W,R,H,T,P,N)
$$
be an accepted $\RealOscillationUp$ carrier. Every $\RealUp$ or Completion-facing read of the oscillation packet factors through the displayed route
$$
O \longmapsto C \longmapsto S \longmapsto D,W,R \longmapsto H,T,P,N \longmapsto X .
$$
Consequently the read receives the CauchyOscillation tail ledger, RealClamping interval route, RegularCauchySqueeze envelope, dyadic tolerance, StreamName window, RegSeqRat readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row before it reaches the Real seal.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project the rows $X,O,C,S,D,W,R,H,T,P,N$. The terminal seal $X$ is present in the packet, but the classifier exposes it to oscillation consumers only through the displayed rows that name the oscillation route.

The read first reaches the tail ledger $O$, then the clamp interval row $C$, and then the squeeze envelope row $S$. These rows supply tail variation, bounded interval routing, and lower-middle-upper enclosure as finite data.

The rows $D,W,R$ provide the shared numerical route. They fix the dyadic tolerance, open the finite StreamName window, and repack the observations as RegSeqRat readback before any Real or Completion-facing conclusion is exposed.

The remaining rows $H,T,P,N$ preserve the same route by transport, replay, provenance, and local naming. No coordinate in the packet can replace that route by ambient Real completeness, quotient stream equality, host trichotomy, a selected limit, or a standard bridge credential, so the displayed factorization is exhaustive.
\end{proof}

\falsifiablePrediction{Every $\RealOscillationUp$ Real or Completion-facing read factors through one CauchyOscillation tail ledger, one RealClamping interval route, one RegularCauchySqueeze envelope, one DyadicRatCore tolerance row, one StreamName window, one RegSeqRat readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, local NameCert, and the terminal RealUp seal.}

\independenceWitness{cauchyoscillation, real-clamping, regular-cauchy-squeeze, dyadicratcore, streamname, regseqrat, real: $\RealOscillationUp$ is not bijective to any listed sibling because it jointly carries a Real seal, an oscillation ledger, a clamp interval route, a squeeze envelope, one shared dyadic-window-readback route, transport, replay, provenance, and local naming.}

\closureat{RealOscillationUp}{seedStr}

\begin{closurestatus}{\RealOscillationUp}
  \constructivestory{A $\RealOscillationUp$ packet is generated from one RealUp seal, one CauchyOscillation ledger, one RealClamping interval row, one RegularCauchySqueeze envelope, one DyadicRatCore tolerance row, one StreamName window, one RegSeqRat readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-oscillation-carrier}, \autoref{thm:real-oscillation-namecert-obligations}, and \autoref{thm:real-oscillation-clamped-window-factorization} seed the finite Real and Completion-facing oscillation route through tail variation, clamping, squeeze enclosure, dyadic tolerance, finite windows, regular rational readback, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.RealOscillationUp.RealOscillationCarrier}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient stream equality, host trichotomy, selected limits, countable choice, Lean theorem checking, or standard bridge credentials.}
  \upgradepath{Obligation closure requires checked carrier admission, oscillation-ledger exposure, clamp interval exposure, squeeze-envelope compatibility, clamped-window factorization, and ledger nonescape for BEDC.Derived.RealOscillationUp.RealOscillationCarrier.}
\end{closurestatus}
