\chapter{A Concrete Naming Certificate for $\CauchySubsequenceExtractionUp$}
\label{ch:concrete-instances-cauchy-subsequence-extraction-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\CauchySubsequenceExtractionUp$ packet records the finite BEDC route by which displayed Cauchy data and an explicit modulus determine a regular observation schedule. It consumes the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Cauchy-sequence boundary of \autoref{ch:concrete-instances-cauchysequencespace-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet names explicit modulus-based subsequence extraction as displayed certificate data, not as a host subsequence function, countable-choice schedule, selected limit, quotient equality, or ambient $\RealUp$ completeness theorem.

\begin{definition}[Cauchy subsequence extraction carrier]
\label{def:cauchy-subsequence-extraction-carrier}
A $\CauchySubsequenceExtractionUp$ carrier is a finite $\BHist$ packet
$$
E=(S,M,D,I,W,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\StreamNameUp$ window row, exposing only finite windows of the Cauchy input stream.
\item $M$ is the explicit Cauchy/modulus row. It records the displayed tolerance request and the stage after which all later source windows satisfy that request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger carrying the dyadic radii, slack comparisons, and budget transfers used by the modulus and extracted windows.
\item $I$ is the increasing index schedule. It is a finite unary trace whose entries are checked to be strictly later and to dominate the stage demanded by $M$ for each displayed tolerance.
\item $W$ is the extracted finite-window ledger, pairing each selected index in $I$ with the source window in $S$ and the dyadic tolerance entry in $D$.
\item $R$ is the $\RegSeqRatUp$ handoff assembled from the extracted windows and the same dyadic tolerance ledger.
\item $H$ records componentwise $\hsame$ transport for the source windows, modulus row, dyadic ledger, index schedule, extracted windows, regular readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite extraction request through $S,M,D,I,W,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchySubsequenceExtractionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchySequenceSpaceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchySubsequenceExtractionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,M,D,I,W,R,H,C,P,N$. It has no coordinate for a host subsequence function, countable-choice selector, selected limit, quotient equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.CauchySubsequenceExtractionUp.CauchySubsequenceExtractionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cauchy subsequence extraction obligation surface]
\label{thm:cauchy-subsequence-extraction-obligation-surface}
For every accepted $\CauchySubsequenceExtractionUp$ carrier
$$
E=(S,M,D,I,W,R,H,C,P,N),
$$
the local $\NameCert_{\CauchySubsequenceExtractionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source stream windows, explicit Cauchy/modulus row, dyadic tolerance ledger, increasing index schedule, extracted window ledger, $\RegSeqRatUp$ handoff, componentwise transport, displayed replay, provenance, and local naming rows;
\item modulus exposure, requiring each finite extraction request to project the displayed Cauchy/modulus row $M$ before reading a selected source window;
\item dyadic budget compatibility, requiring the tolerance entry in $D$ used by $M$ to be the same entry consumed by the extracted window ledger $W$ and the regular readback $R$;
\item schedule monotonicity, requiring $I$ to be a finite increasing unary trace whose chosen indices dominate the displayed modulus stage for the relevant tolerance;
\item extracted-window exactness, requiring $W$ to pair only windows from $S$ with indices admitted by $I$ and tolerances recorded in $D$;
\item regular handoff, requiring $R$ to be assembled from the extracted windows and tolerance ledger rather than from a detached stream representative;
\item non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no host subsequence function, countable-choice selector, selected limit, quotient equality, ambient Real-completeness datum, Lean credential, or bridge credential.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-subsequence-extraction-carrier}. The analytic rows are exactly the source windows $S$, modulus row $M$, dyadic ledger $D$, increasing index schedule $I$, extracted window ledger $W$, and regular readback row $R$.

The modulus and dyadic obligations are row-local. A finite extraction request must first read $M$, and the tolerance entry it names is the same dyadic budget recorded in $D$ for the extracted windows and the downstream regular readback.

Schedule monotonicity is read from $I$. Since $I$ is a finite unary trace inside the packet, the certificate checks increasingness and domination of the displayed modulus stage without selecting an infinite subsequence function.

Extracted-window exactness and the regular handoff are the projections to $W$ and $R$. The ledger $W$ can pair only indices admitted by $I$ with source windows from $S$, and $R$ is assembled from those displayed windows under the same tolerance data.

The remaining rows are structural. Componentwise transport, continuation replay, provenance, and the local name preserve only the displayed packet rows, so no excluded host selector, selected limit, quotient equality, ambient completeness claim, Lean credential, or bridge credential can enter the local surface.
\end{proof}

\begin{theorem}[Cauchy subsequence extraction regular window bound]
\label{thm:cauchy-subsequence-extraction-regular-window}
Let $E=(S,M,D,I,W,R,H,C,P,N)$ be an accepted $\CauchySubsequenceExtractionUp$ carrier. For every displayed dyadic tolerance request in $D$, each extracted window in $W$ whose selected index is admitted by $I$ and dominates the corresponding stage of $M$ is bounded by the same regular tolerance budget used by the $\RegSeqRatUp$ row $R$.
\end{theorem}
\begin{proof}
Fix a displayed dyadic tolerance request in $D$. The carrier admits no tolerance row other than $D$, so both the modulus row and the extracted-window ledger must read the same budget.

The row $M$ supplies the stage after which the source stream windows meet the requested Cauchy bound. The row $I$ supplies a finite increasing trace whose selected entry dominates that stage.

Now project $W$. Each extracted window recorded in $W$ is paired with an admitted index from $I$ and with the same dyadic tolerance entry from $D$, so the Cauchy bound supplied by $M$ applies to that extracted window.

Finally project $R$. The regular rational handoff is assembled from the extracted windows and tolerance ledger already read by $W$, hence it uses exactly the same regular budget and cannot tighten or replace it through a detached representative.
\end{proof}

\begin{theorem}[Cauchy subsequence extraction RegSeqRat handoff]
\label{thm:cauchy-subsequence-extraction-regseqrat-handoff}
Every $\RegSeqRatUp$-facing read exported by an accepted $\CauchySubsequenceExtractionUp$ carrier
$$
E=(S,M,D,I,W,R,H,C,P,N)
$$
factors through the finite chain
$$
S \longmapsto M \longmapsto D \longmapsto I \longmapsto W \longmapsto R
$$
before it can inspect the structural rows $H,C,P,N$. Consequently the handoff exports finite stream windows, an explicit modulus row, dyadic tolerance data, an increasing index schedule, extracted windows, and a regular rational readback, but no host subsequence function, countable-choice selector, selected limit, quotient equality, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with a $\RegSeqRatUp$-facing read of the accepted packet. The source surface available to the read is the finite stream-window row $S$.

The request then projects $M$ and $D$. These rows display the Cauchy/modulus stage and the dyadic tolerance ledger that the extracted schedule must respect.

The increasing schedule $I$ is consumed next. It supplies only a finite unary trace, so the read obtains selected positions for the displayed request without importing a host subsequence function or countable-choice selector.

The extracted-window ledger $W$ pairs those selected positions with source windows and dyadic tolerances. The $\RegSeqRatUp$ row $R$ is assembled from that ledger, and no coordinate allows a detached stream representative or quotient equality to replace it.

Only after this chain has been read may the structural rows $H,C,P,N$ transport, replay, source, and name the packet. They preserve the same displayed route and do not export selected limits or ambient Real completeness.
\end{proof}

\closureat{CauchySubsequenceExtractionUp}{seedStr}

\begin{closurestatus}{\CauchySubsequenceExtractionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-subsequence-extraction-carrier}, \autoref{thm:cauchy-subsequence-extraction-obligation-surface}, \autoref{thm:cauchy-subsequence-extraction-regular-window}, and \autoref{thm:cauchy-subsequence-extraction-regseqrat-handoff} seed the finite explicit-modulus extraction route from stream windows through dyadic tolerances, increasing schedules, extracted windows, and RegSeqRat readback.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.CauchySubsequenceExtractionUp.CauchySubsequenceExtractionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host subsequence functions, countable choice, selected limits, quotient equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus exposure, dyadic budget compatibility, schedule monotonicity, extracted-window exactness, regular-window bounds, RegSeqRat handoff, and non-escape proofs for BEDC.Derived.CauchySubsequenceExtractionUp.}
  \constructivestory{A $\CauchySubsequenceExtractionUp$ packet is generated from source StreamName windows, an explicit Cauchy/modulus row, a DyadicRatCore tolerance ledger, an increasing index schedule, extracted finite windows, a RegSeqRat handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
