\chapter{A Concrete Naming Certificate for $\DyadicGeometricTailUp$}
\label{ch:concrete-instances-dyadic-geometric-tail-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DyadicGeometricTailUp$ packet records the finite modulus certificate for a dyadic geometric tail whose ratio is displayed below the unit scale. It sits over the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the partial-sum surface of \autoref{ch:concrete-instances-realseries-namecert}. The packet supplies the L10 regular-Cauchy route with a named finite carrier for ratio-test, power-series, and convergence-radius consumers; it is not an infinite geometric series theorem, a selected real limit, a quotient of streams, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Dyadic geometric tail carrier]
\label{def:dyadic-geometric-tail-carrier}
A $\DyadicGeometricTailUp$ carrier is a finite $\BHist$ packet
$$
G=(q,n,W,D,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $q$ is the dyadic ratio row. It records a displayed dyadic rational ratio together with a finite witness that the ratio lies strictly below the unit tolerance scale.
\item $n$ is the unary exponent window. It records the displayed starting exponent, the inspected precision request, and the finite induction spine over which powers of $q$ are unfolded.
\item $W$ is the finite $\StreamNameUp$ window family on which the ratio row, exponent row, tail ledger, regular readback, and endpoint seal are read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It stores the dyadic arithmetic used to compare each displayed tail bound with the requested tolerance.
\item $T$ is the finite geometric tail row. It records the displayed numerator power, denominator slack, and finite inequality chain for the tail beginning at the exponent row $n$.
\item $R$ is the $\RegSeqRatUp$ readback row. It exports the displayed tail bound as a regular rational modulus row for downstream Cauchy consumers.
\item $E$ is the $\RealUp$ endpoint seal. It records the Real-facing endpoint only after the dyadic tail and regular readback rows have been inspected.
\item $H$ records componentwise $\hsame$ transport for the dyadic ratio, exponent window, stream windows, dyadic ledger, tail row, regular readback, endpoint seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a precision request through $q,n,W,D,T$ to the $\RegSeqRatUp$ row $R$ and then to the $\RealUp$ seal $E$.
\item $P$ is the $\Pkg$ provenance over $\DyadicGeometricTailUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealSeriesUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicGeometricTailUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these displayed rows. It has no coordinate for an unbounded exponent search, a host real geometric-series formula, quotient stream equality, selected completed limits, countable choice, or ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.DyadicGeometricTailUp.TasteGate.DyadicGeometricTailTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Dyadic geometric tail NameCert obligations]
\label{thm:dyadic-geometric-tail-namecert-obligations}
For every accepted $\DyadicGeometricTailUp$ carrier $G=(q,n,W,D,T,R,E,H,C,P,N)$, the local $\NameCert_{\DyadicGeometricTailUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed eleven-row packet;
\item ratio exposure for $q$, including the displayed dyadic ratio and the strict-below-unit witness;
\item unary exponent exposure for $n$, including the finite starting exponent and the induction window selected by the precision request;
\item window admission for $W$, requiring every source, ledger, tail, readback, and endpoint read to occur on one of the displayed $\StreamNameUp$ windows;
\item dyadic tolerance exactness for $D$, requiring the requested tolerance comparison to be carried by displayed $\DyadicRatCoreUp$ arithmetic;
\item geometric tail exposure for $T$, requiring the numerator power, denominator slack, and finite inequality chain to be displayed before any modulus is exported;
\item regular readback and endpoint sealing through $R$ and $E$;
\item transport stability, continuation replay, provenance, and local naming for exactly the route recorded by $H,C,P,N$.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier $G=(q,n,W,D,T,R,E,H,C,P,N)$. The projection exposes exactly the dyadic ratio row, unary exponent row, finite windows, dyadic ledger, geometric tail row, regular readback, endpoint seal, transport rows, continuation replay, provenance, and local naming row.

The ratio and exponent obligations are read first. The row $q$ supplies the displayed dyadic ratio and its strict-below-unit witness, while $n$ supplies the finite unary spine on which powers of $q$ are unfolded for the requested tolerance.

The arithmetic obligations are read next. The windows $W$ restrict all source reads to finite $\StreamNameUp$ data, and the ledger $D$ carries the dyadic comparison between the displayed tail row $T$ and the requested tolerance scale.

Finally the structural rows close the surface. The rows $R$ and $E$ are downstream readbacks of the same displayed tail estimate, while $H,C,P,N$ only transport, replay, source, and name that route. Since the packet has no additional coordinate, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Dyadic geometric tail modulus]
\label{thm:dyadic-geometric-tail-modulus}
Every accepted $\DyadicGeometricTailUp$ carrier exports a finite modulus route
$$
q,n,W,D,T\longmapsto R
$$
such that each displayed precision request is answered by a finite exponent threshold whose dyadic geometric tail row is below the requested $\DyadicRatCoreUp$ tolerance. The construction uses only the strict-below-unit witness in $q$ and finite unary induction over the exponent window $n$.
\end{theorem}
\begin{proof}
Fix an accepted carrier and a displayed precision request. Read $q$ to obtain the dyadic ratio and the strict-below-unit witness, then read $n$ to obtain the finite unary exponent window selected for that request.

Proceed by finite unary induction along the window $n$. At the base exponent, the tail row $T$ displays the initial numerator power and denominator slack. At each successor exponent, multiply by the displayed ratio row $q$ and use the strict-below-unit witness to preserve the dyadic domination direction.

The ledger $D$ records each arithmetic comparison against the requested tolerance. Because the induction window is finite and every dyadic comparison is displayed in $D$, the final row of $T$ supplies a finite threshold whose tail estimate is below the requested tolerance.

Export the threshold through $R$. The regular rational readback row does not add a limit or a host series theorem; it only repackages the displayed dyadic tail estimate as the modulus row expected by downstream regular-Cauchy consumers.
\end{proof}

\begin{theorem}[Dyadic geometric tail RegSeqRat handoff]
\label{thm:dyadic-geometric-tail-regseqrat-handoff}
Every accepted $\DyadicGeometricTailUp$ carrier hands a modulus to $\RegSeqRatUp$ only through the displayed route
$$
q,n,W,D,T\longmapsto R\longmapsto E,H,C,P,N.
$$
Consequently any $\RealSeriesUp$, ratio-test, power-series, or convergence-radius consumer must read the dyadic ratio row, unary exponent window, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, finite geometric tail row, and $\RegSeqRatUp$ readback before using the Real-facing endpoint seal.
\end{theorem}
\begin{proof}
Begin with an accepted carrier. The NameCert obligation surface of \autoref{thm:dyadic-geometric-tail-namecert-obligations} makes $R$ the only row that exports the displayed tail estimate as a regular rational modulus.

The handoff is therefore forced through the dyadic route. A consumer must first read the ratio row $q$, the exponent window $n$, the source windows $W$, the tolerance ledger $D$, and the geometric tail row $T$ before the regular readback row $R$ is available.

Transport preserves the same route. The componentwise $\hsame$ entries in $H$ carry the dyadic ratio, exponent window, ledger, tail estimate, regular readback, and endpoint seal together, so a transported carrier cannot replace the finite tail calculation with a host analytic formula.

The continuation, provenance, and local naming rows only replay and name the displayed route. Hence $\RealSeriesUp$, ratio-test, power-series, and convergence-radius consumers receive a $\RegSeqRatUp$ handoff exactly through $q,n,W,D,T,R,E,H,C,P,N$.
\end{proof}

\falsifiablePrediction{An accepted $\DyadicGeometricTailUp$ consumer that reads a $\RegSeqRatUp$ or $\RealUp$ conclusion without the displayed dyadic ratio row, unary exponent window, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ ledger, geometric tail row, and regular readback row refutes the carrier surface.}

\independenceWitness{dyadicratcore, streamname, regseqrat, realseries: no listed sibling supplies the whole eleven-row packet $G=(q,n,W,D,T,R,E,H,C,P,N)$, because each sibling contributes only a dyadic arithmetic face, finite window face, regular readback face, or series consumer face while this chapter binds the geometric-tail modulus route with transport, replay, provenance, and local naming.}

\closureat{DyadicGeometricTailUp}{seedStr}

\begin{closurestatus}{\DyadicGeometricTailUp}
  \constructivestory{A $\DyadicGeometricTailUp$ packet is generated from a dyadic ratio row below the unit scale, a unary exponent window, finite $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ tolerance ledger, a finite geometric tail row, a $\RegSeqRatUp$ readback row, a $\RealUp$ endpoint seal, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-geometric-tail-carrier}, \autoref{thm:dyadic-geometric-tail-namecert-obligations}, \autoref{thm:dyadic-geometric-tail-modulus}, and \autoref{thm:dyadic-geometric-tail-regseqrat-handoff} seed the finite geometric-tail modulus interface from dyadic ratio rows to $\RegSeqRatUp$ and $\RealSeriesUp$ consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a host geometric-series theorem, quotient stream equality, selected completed limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, ratio exposure, unary exponent induction, dyadic tolerance exactness, regular readback, endpoint sealing, provenance exhaustion, and local naming for BEDC.Derived.DyadicGeometricTailUp.}
\end{closurestatus}
