\chapter{A Concrete Naming Certificate for $\LocatedUniformContinuityUp$}
\label{ch:concrete-instances-located-uniform-continuity-namecert}
\origin{human}

Following Bishop and Bridges on constructive continuity with explicit moduli, the $\LocatedUniformContinuityUp$ packet records the finite L10 route by which a located source row and a located-apartness witness feed a uniform-continuity modulus before any Real or completion consumer reads the target seal. It sits over the modulus discipline of \autoref{ch:concrete-instances-moduluscontinuity-namecert}, the Cauchy-modulus row of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the completion handoff of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, and the located-source surface of \autoref{ch:concrete-instances-locatedset-namecert}. The packet names the constructive located-uniform-continuity handoff; it is not open-cover compactness, host function equality, selected limits, quotient stream equality, countable choice, or ambient Real completeness.

\begin{definition}[Located uniform continuity carrier]
\label{def:located-uniform-continuity-carrier}
A $\LocatedUniformContinuityUp$ carrier is a finite $\BHist$ packet
$$
L=(X,A,M,S,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the located source row, exposing the finite $\LocatedSetUp$ cells and source-location requests that the continuity route may inspect.
\item $A$ is the located-apartness witness row, recording the positive separation and located decision cells used to keep source inspection constructive.
\item $M$ is the $\ModulusContinuityUp$ row, turning each requested target tolerance into a finite source-window budget and citing the Cauchy-modulus discipline when completion-facing reads ask for tail control.
\item $S$ is the $\StreamNameUp$ finite-window row consumed by the located source, apartness, and modulus rows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording target tolerances, source budgets, dyadic endpoints, comparison cells, and positive-gap readbacks.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same windows and dyadic ledger.
\item $E$ is the $\RealUp$ and $\BishopRegularCauchyCompletionUp$ seal handoff, visible only after $X,A,M,S,D,R$ have fixed the displayed route.
\item $H$ records componentwise $\hsame$ transport for the located source, apartness witness, modulus row, windows, dyadic ledger, regular readback, Real and completion handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located-uniform-continuity request through source location, apartness inspection, modulus conversion, finite-window readback, dyadic ledger inspection, regular readback, and completion handoff.
\item $P$ is the $\Pkg$ provenance over $\LocatedUniformContinuityUp$, $\LocatedSetUp$, $\ModulusContinuityUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRegularCauchyCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedUniformContinuityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,A,M,S,D,R,E,H,C,P,N$. It has no coordinate for open-cover compactness, host function equality, selected limits, quotient stream equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.LocatedUniformContinuityUp.LocatedUniformContinuityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located uniform continuity NameCert obligations]
\label{thm:located-uniform-continuity-namecert-obligations}
For every accepted $\LocatedUniformContinuityUp$ carrier
$$
L=(X,A,M,S,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedUniformContinuityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located source, located-apartness witness, modulus-continuity row, StreamName finite windows, DyadicRatCore tolerance ledger, RegSeqRat readback, Real and completion seal handoff, transport, replay, provenance, and local naming;
\item located-source stability, requiring $X$ and $A$ to expose only displayed source cells and positive-separation witnesses before any target tolerance can be read;
\item modulus-window adequacy, requiring $M,S,D$ to turn every target tolerance into a finite source-window budget recorded in the dyadic ledger;
\item readback and handoff coherence, requiring $R$ and $E$ to consume the same windows and budgets before any Real or completion-facing consumer receives a seal;
\item transport, replay, and non-escape, requiring $H,C,P,N$ to preserve only the displayed rows and to export no open-cover compactness, host function equality, selected limit, quotient stream equality, countable choice, or ambient Real completeness.
\end{enumerate}
No local located-uniform-continuity obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-uniform-continuity-carrier}. The accepted packet displays exactly the located source row, apartness witness, modulus row, finite windows, dyadic ledger, regular readback, Real and completion handoff, and the structural rows.

Located-source stability is forced by the order of the displayed route. The rows $X$ and $A$ are read before any tolerance request reaches $M$, so source inspection remains located and positive-separation evidence cannot be replaced by a host equality test.

The modulus-window obligation is the finite handoff through $M,S,D$. A target tolerance first reads the modulus row, then opens only the source windows in $S$ and the dyadic cells in $D$ that were displayed for that request.

Readback and handoff coherence are projections to $R$ and $E$. The regular rational row and the Real or completion seal consume the same windows and budgets, so neither can select a limit, compare quotient streams, or import ambient completeness.

Finally, $H,C,P,N$ transport, replay, source, and name the same finite route. Since the excluded principles have no coordinate in the carrier, they cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[Located uniform continuity completion handoff]
\label{thm:located-uniform-continuity-completion-handoff}
Every Real or completion consumer of an accepted $\LocatedUniformContinuityUp$ carrier factors through the displayed route
$$
X,A,M,S,D \longmapsto R \longmapsto E
$$
before componentwise transport, replay, provenance, or local naming can be inspected. The consumer receives a located source, located-apartness evidence, an explicit modulus, finite windows, a dyadic tolerance ledger, regular rational readback, and a Real or Bishop-regular-Cauchy completion seal, but no selected limit, quotient stream equality, countable choice, host function equality, open-cover compactness, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $L=(X,A,M,S,D,R,E,H,C,P,N)$. Projection exposes the located source row $X$ and the apartness witness row $A$ before any completion-facing read is available.

The modulus stage is next. The row $M$ turns the target request into source-window data, and those windows are exactly the finite cells recorded by $S$ and budgeted by the dyadic ledger $D$.

The regular readback row $R$ consumes the same finite data. It does not choose a stream representative or a limiting value; it records the regular rational readback allowed by the displayed source windows and tolerance ledger.

The handoff row $E$ is terminal for Real and completion consumers. It receives $X,A,M,S,D,R$ as finite BEDC rows and has no coordinate for selected limits, quotient equality, choice, host function equality, open-cover compactness, or ambient completeness.

The structural rows $H,C,P,N$ preserve this route by componentwise transport, displayed replay, provenance, and local naming. Therefore every Real or completion consumer factors through the displayed handoff before it can inspect the terminal certificate surface.
\end{proof}

\begin{theorem}[Located uniform continuity non-escape]
\label{thm:located-uniform-continuity-nonescape}
No accepted $\LocatedUniformContinuityUp$ packet exports open-cover compactness, host function equality, selected limits, quotient stream equality, countable choice, or ambient $\RealUp$ completeness. Every exported comparison, replay, or consumer handoff is exhausted by the rows $X,A,M,S,D,R,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Inspect the classifier of \autoref{def:located-uniform-continuity-carrier}. Accepted packets are compared only componentwise through the displayed located source, apartness, modulus, window, ledger, readback, seal, transport, replay, provenance, and naming rows.

The analytic rows $X,A,M,S,D,R,E$ provide located source inspection, positive separation, tolerance conversion, finite windows, dyadic budgets, regular readback, and terminal Real or completion handoff. None stores an open cover, a host function graph equality, a chosen limit, a quotient-stream equality proof, a choice schedule, or an ambient completeness principle.

The structural rows $H,C,P,N$ cannot add new analytic coordinates. They transport, replay, source, and name only the accepted tuple, so any exported comparison or consumer handoff must remain inside the same finite row list.

Thus the excluded principles have no entry point in the carrier, classifier, transport, replay, provenance, or local NameCert surface, and the packet is non-escaping in precisely the stated sense.
\end{proof}

\closureat{LocatedUniformContinuityUp}{seedStr}

\begin{closurestatus}{\LocatedUniformContinuityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-uniform-continuity-carrier}, \autoref{thm:located-uniform-continuity-namecert-obligations}, \autoref{thm:located-uniform-continuity-completion-handoff}, and \autoref{thm:located-uniform-continuity-nonescape} seed the finite Real and Completion route for located-source uniform continuity through located source, apartness, modulus, finite-window, dyadic-ledger, regular-readback, Real and completion handoff, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, host function equality, selected limits, quotient stream equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires the later BEDC.Derived.LocatedUniformContinuityUp carrier, modulus-window, completion-handoff, transport, and nonescape obligations.}
  \constructivestory{A $\LocatedUniformContinuityUp$ packet is generated from a $\LocatedSetUp$ source row, a located-apartness witness row, a $\ModulusContinuityUp$ row citing $\CauchyModulusUp$ tail control, $\StreamNameUp$ finite windows, a $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, a $\RealUp$ and $\BishopRegularCauchyCompletionUp$ handoff seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
