\chapter{A Concrete Naming Certificate for $\CauchyProductModulusUp$}
\label{ch:concrete-instances-cauchy-product-modulus-namecert}
\origin{human}

Following Bishop and Bridges, the $\CauchyProductModulusUp$ packet records the finite modulus calculation that turns two regular rational Cauchy source moduli into a displayed product tolerance. It reads the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic endpoint arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the product-budget ledger of \autoref{ch:concrete-instances-regularcauchyproductbudget-namecert}, the multiplication route of \autoref{ch:concrete-instances-regular-cauchy-multiplication-namecert}, and the terminal field-facing boundary of \autoref{ch:concrete-instances-cauchy-real-field-namecert}. The certificate is a named finite product-modulus bridge; it is not host real multiplication, quotient stream equality, a selected limit, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy product modulus carrier]
\label{def:cauchy-product-modulus-carrier}
A $\CauchyProductModulusUp$ carrier is a finite $\BHist$ packet
$$
Q=(A,B,W_A,W_B,D_A,D_B,E,M,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two accepted source modulus rows attached to the regular rational Cauchy names whose product is being certified.
\item $W_A$ and $W_B$ are the paired $\StreamNameUp$ windows opened from the two sources at the product-facing precision request.
\item $D_A$ and $D_B$ are the $\DyadicRatCoreUp$ endpoint, radius, and bound rows read from those finite windows.
\item $E$ is the $\RegularCauchyProductBudgetUp$ ledger that assigns the source-window tolerances, dyadic product allowance, and remaining readback budget.
\item $M$ is the product modulus row, computed from $A,B,W_A,W_B,D_A,D_B,E$ and recording the output precision request together with the finite source-window budgets that answer it.
\item $R$ is the $\RegSeqRatUp$ handoff row that consumes the product modulus row as the regular rational product readback.
\item $S$ is the $\RealUp$ seal row through which the Cauchy real field surface may inspect the product only after the finite modulus and readback rows have been displayed.
\item $H$ stores componentwise $\hsame$ transports for the two source moduli, paired windows, dyadic bounds, product-budget ledger, modulus row, readback, seal, provenance, and local naming row.
\item $C$ stores displayed $\Cont$ replay from a product precision request through the two source windows, dyadic rows, budget ledger, product modulus row, readback, seal, and structural rows.
\item $P$ is the $\Pkg$ provenance over $\CauchyProductModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RegularCauchyProductBudgetUp$, $\RegularCauchyMultiplicationUp$, $\CauchyRealFieldUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyProductModulusUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the displayed rows $A,B,W_A,W_B,D_A,D_B,E,M,R,S,H,C,P,N$. The carrier contains no coordinate for host real multiplication, quotient streams, selected limits, ambient Real completeness, or a hidden product-modulus oracle.
\end{definition}
\leanchecked{BEDC.Derived.CauchyProductModulusUp.CauchyProductModulusTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cauchy product modulus window budget]
\label{thm:cauchy-product-modulus-window-budget}
Let
$$
Q=(A,B,W_A,W_B,D_A,D_B,E,M,R,S,H,C,P,N)
$$
be an accepted $\CauchyProductModulusUp$ carrier. Every product tolerance requested from $Q$ factors through the displayed source-window budgets $W_A,W_B$, the dyadic bound rows $D_A,D_B$, and the existing product-budget ledger $E$ before the product modulus row $M$ can be read. Consequently the exported $\RegSeqRatUp$ product handoff $R$ receives its tolerance only from the finite route
$$
A,B,W_A,W_B,D_A,D_B,E,M.
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-product-modulus-carrier}. The only source observations available to a product precision request are the two source modulus rows and the paired finite windows $W_A,W_B$.

Read the dyadic rows $D_A,D_B$. They supply the finite endpoint, radius, and bound data used by the product calculation, so the product tolerance cannot be allocated before those rows are displayed.

Now inspect the ledger coordinate $E$. By definition it is the $\RegularCauchyProductBudgetUp$ ledger binding the two source-window tolerances, the dyadic product allowance, and the remaining readback budget. The product modulus row $M$ is downstream of this ledger, and the readback $R$ is downstream of $M$.

Thus every product tolerance exported by the packet factors through $A,B,W_A,W_B,D_A,D_B,E,M$, and no other row can supply the requested product budget.
\end{proof}

\begin{theorem}[Cauchy product modulus NameCert obligations]
\label{thm:cauchy-product-modulus-namecert-obligations}
For every accepted $\CauchyProductModulusUp$ carrier
$$
Q=(A,B,W_A,W_B,D_A,D_B,E,M,R,S,H,C,P,N),
$$
the local $\NameCert_{\CauchyProductModulusUp}$ surface consists exactly of the following five rows:
\begin{enumerate}
\item carrier admission for the two source moduli, paired source windows, dyadic bound rows, product-budget ledger, product modulus row, $\RegSeqRatUp$ handoff, $\RealUp$ seal, and structural rows;
\item window-budget exactness, requiring each product tolerance to pass through $W_A,W_B,D_A,D_B,E$ before $M$ is available;
\item product-modulus handoff, requiring $M$ to be the sole row from which the $\RegSeqRatUp$ product readback $R$ receives its output tolerance;
\item Real seal boundary, requiring every field-facing read to reach $S$ only after the finite product modulus route has produced $R$;
\item transport, replay, provenance, and local naming stability through $H,C,P,N$, with no escape to host real multiplication, quotient streams, selected limits, ambient $\RealUp$ completeness, or any hidden external product-modulus choice.
\end{enumerate}
No NameCert obligation for this packet is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductModulusUp.TasteGate.CauchyProductModulusCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is the tuple in \autoref{def:cauchy-product-modulus-carrier}. It lists all accepted coordinates of the packet and makes no additional source of product information available.

Window-budget exactness is \autoref{thm:cauchy-product-modulus-window-budget}. The requested tolerance reaches the product modulus row only through the paired windows, dyadic bound rows, and the product-budget ledger.

The product-modulus handoff follows from the position of $M$ and $R$ in the carrier. Since $R$ is the only $\RegSeqRatUp$ product readback row and it is downstream of $M$, the handoff cannot bypass the displayed modulus row.

The Real seal boundary is the projection to $S$. That row is reached after $R$, so a field-facing read remains downstream of the finite product modulus route.

Finally, $H,C,P,N$ transport, replay, source, and name the same displayed packet. Because no coordinate stores host multiplication, quotient stream equality, selected limits, ambient completeness, or an external choice of modulus, the non-escape clauses follow by inspection.
\end{proof}

\closureat{CauchyProductModulusUp}{seedStr}

\begin{closurestatus}{\CauchyProductModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-product-modulus-carrier}, \autoref{thm:cauchy-product-modulus-window-budget}, and \autoref{thm:cauchy-product-modulus-namecert-obligations} seed the finite product-modulus carrier between product-budget accounting, regular rational product readback, and the Real field seal.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.CauchyProductModulusUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real multiplication, quotient stream equality, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, product-budget handoff, modulus exactness, RegSeqRat handoff, and Real seal non-escape for the same finite packet.}
  \constructivestory{A $\CauchyProductModulusUp$ packet is generated from two source modulus rows, paired StreamName windows, DyadicRatCore bound rows, a RegularCauchyProductBudget ledger, a product modulus row, a RegSeqRat product readback, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
