\chapter{A Concrete Naming Certificate for $\CousinLemmaUp$}
\label{ch:concrete-instances-cousin-lemma-namecert}
\origin{human}

Following Bishop-style treatments of Cousin's lemma for gauge partitions, the $\CousinLemmaUp$ packet names the finite route from a located closed interval and a displayed positive gauge to a tagged interval subdivision. It sits between the finite cover surface of \autoref{ch:concrete-instances-interval-finite-cover-certificate-namecert}, the positive-radius handoff of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, and the bisection discipline of \autoref{ch:concrete-instances-located-interval-bisection-namecert}. Its Real-facing rows are read through the finite $\StreamNameUp$ windows of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The chapter records the traditional finite-subdivision certificate used by later integration and compact-interval cover arguments; it is not general open-cover compactness, a choice-selected partition, or host real completeness.

\begin{definition}[Cousin lemma carrier]
\label{def:cousin-lemma-carrier}
A $\CousinLemmaUp$ carrier is a finite $\BHist$ packet
$$
K=(I,G,T,M,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the located closed interval row, including the named endpoints, endpoint order, and the interval boundary that later bisection rows may inspect.
\item $G$ is the gauge row, assigning to each displayed tag request a positive local radius read through finite rational and Real-facing witnesses.
\item $T$ is the finite tagged-subinterval row. Each entry records a tag, a left endpoint, a right endpoint, adjacency to the neighbouring row, containment in $I$, and the local gauge admission for that tag.
\item $M$ is the mesh ledger recording the endpoint comparisons and mesh bounds used to certify that consecutive tagged subintervals cover exactly the displayed interval row.
\item $W$ is the located bisection ledger. It records the finite bisection induction tree that refines any row whose current mesh is not yet admitted by the corresponding gauge radius.
\item $R$ is the $\StreamNameUp$ window schedule exposed for the endpoint, tag, radius, and mesh observations in $I,G,T,M,W$.
\item $E$ is the $\RegSeqRatUp$ readback and terminal $\RealUp$ seal reached only after the finite window schedule has been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval, gauge, tagged-subdivision, mesh, bisection, window, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a gauge-partition request through $I,G,W,T,M,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CousinLemmaUp$, $\IntervalFiniteCoverCertificateUp$, $\FiniteLebesgueNumberUp$, $\LocatedIntervalBisectionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CousinLemmaUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,G,T,M,W,R,E,H,C,P,N$. It has no coordinate for a general open-cover compactness theorem, a choice-selected partition, a host real completeness theorem, quotient stream equality, or an external real interval object.
\end{definition}
\leanchecked{BEDC.Derived.CousinLemmaUp.TasteGate.CousinLemmaTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Cousin lemma NameCert obligations]
\label{thm:cousin-lemma-namecert-obligations}
For every accepted $\CousinLemmaUp$ carrier
$$
K=(I,G,T,M,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\CousinLemmaUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed located interval, gauge, tagged-subdivision, mesh, bisection, window, readback, Real-seal, transport, replay, provenance, and local naming rows;
\item gauge positivity and locality, requiring every tag row of $T$ to read its radius from $G$ and to prove the corresponding tagged subinterval is contained in that local radius window;
\item subdivision adjacency and coverage, requiring the ordered entries of $T$ to start at the left endpoint of $I$, end at the right endpoint of $I$, and share consecutive endpoints without gaps or overlaps;
\item mesh and bisection exactness, requiring $M$ and $W$ to be the only ledgers by which failed local gauge tests are refined into smaller interval rows;
\item StreamName, RegSeqRat, and Real-seal discipline, requiring $R$ and $E$ to read only the finite endpoint, tag, radius, and mesh windows already exposed by $I,G,T,M,W$;
\item structural non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no general open-cover compactness theorem, choice-selected partition, host real completeness theorem, quotient stream equality, or external real interval object.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cousin-lemma-carrier}. The accepted packet displays the located interval, gauge, tagged subdivision, mesh ledger, bisection ledger, finite window schedule, readback and Real seal, and the structural rows.

Gauge positivity and locality are read from $G$ and $T$. Each tag row carries its own local radius test, and the classifier has no branch that can replace that test by an arbitrary open cover or by a selected point from the ambient host interval.

Subdivision adjacency and coverage are read from $T$ and $M$. The first and last endpoint comparisons bind the subdivision to $I$, while consecutive endpoint equality is recorded in the finite mesh ledger.

The refinement surface is exhausted by $W$. Whenever a current interval row does not satisfy its local gauge test, the next row is produced by the displayed bisection ledger and then re-tested through the same gauge row.

Finally $R,E,H,C,P,N$ preserve this route. The StreamName windows and RegSeqRat readback use only the displayed finite observations, the Real seal is terminal for those observations, and the structural rows transport and name the same packet. Since no excluded coordinate occurs in the carrier, the listed rows are exactly the NameCert obligations.
\end{proof}

\begin{theorem}[Cousin tagged partition existence]
\label{thm:cousin-lemma-tagged-partition-existence}
Let $K=(I,G,T,M,W,R,E,H,C,P,N)$ be an accepted $\CousinLemmaUp$ carrier. The tagged-subinterval row $T$ is produced by finite bisection induction over the displayed located interval row $I$: the base row accepts an interval whose chosen tag radius from $G$ covers the current subinterval, and the induction row bisects a failed interval by $W$, applies the same local gauge test to both children, and concatenates the accepted child rows with the adjacency ledger in $M$. Thus $T$ is a finite tagged partition of $I$ whose every tagged subinterval is admitted by its own gauge row.
\end{theorem}
\begin{proof}
Proceed by finite induction on the bisection tree displayed in $W$. The base case is an interval row already admitted by its local gauge radius in $G$. Its single tagged subinterval is entered into $T$, and $M$ records that its endpoints are the endpoints of the current interval.

For the induction step, take a displayed interval row whose local gauge test has not yet been admitted. The bisection ledger $W$ supplies the midpoint row and the two child interval rows, both still contained in the parent row of $I$.

Apply the induction hypothesis separately to the left and right child rows. The left accepted list covers the left child, the right accepted list covers the right child, and every row in both lists carries its own tag and gauge-radius admission from $G$.

Concatenate the two finite lists. The mesh ledger $M$ identifies the shared midpoint endpoint and preserves the outer endpoints inherited from the parent interval. This gives a finite tagged partition of the parent row.

Applying this construction to the root interval row $I$ yields the displayed row $T$. The proof uses only the finite bisection induction ledger, not open-cover compactness or countable choice.
\end{proof}

\begin{theorem}[Cousin finite Lebesgue handoff]
\label{thm:cousin-lemma-finite-lebesgue-handoff}
Every $\FiniteLebesgueNumberUp$, Riemann-style, Darboux-style, compact-interval-cover, or Real-completion consumer of an accepted $\CousinLemmaUp$ carrier reads the packet through the ordered route
$$
I,G,W,T,M \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
The exported handoff is a finite gauge-tagged subdivision certificate over displayed interval rows, StreamName windows, RegSeqRat readback, and the terminal $\RealUp$ seal. It does not export general open-cover compactness, choice-selected partitions, host real completeness, quotient stream equality, or external interval equality.
\end{theorem}
\begin{proof}
Start with a downstream consumer read. Carrier admission exposes the located interval row $I$ and the gauge row $G$ before any subdivision data can be inspected.

The bisection ledger $W$ and tagged-subinterval row $T$ then provide the finite subdivision route. The mesh ledger $M$ records the endpoint comparisons and adjacency facts consumed by finite Lebesgue-number, Riemann-style, Darboux-style, and compact-interval-cover arguments.

The Real-facing part of the read passes next through $R$ and $E$. These rows expose only finite StreamName windows, RegSeqRat readback, and the terminal Real seal attached to the interval, tag, radius, and mesh observations already displayed.

The remaining rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since the carrier has no coordinate for open-cover compactness, a choice-selected partition, host real completeness, quotient stream equality, or external interval equality, no downstream consumer can read those principles from the handoff.
\end{proof}

\closureat{CousinLemmaUp}{seedStr}

\begin{closurestatus}{\CousinLemmaUp}
  \constructivestory{A $\CousinLemmaUp$ packet is generated from a located closed interval row, a positive gauge row, finite tagged-subinterval rows, mesh and bisection ledgers, finite StreamName windows, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cousin-lemma-carrier}, \autoref{thm:cousin-lemma-namecert-obligations}, \autoref{thm:cousin-lemma-tagged-partition-existence}, and \autoref{thm:cousin-lemma-finite-lebesgue-handoff} seed the finite gauge-tagged subdivision route from a located closed interval through bisection induction, StreamName windows, RegSeqRat readback, and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.CousinLemmaUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close general open-cover compactness, choice-selected partitions, host real completeness, quotient stream equality, external interval equality, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, gauge locality, subdivision adjacency, finite bisection induction, finite Lebesgue handoff, Real-seal non-escape, and downstream consumer boundary proofs for BEDC.Derived.CousinLemmaUp.}
\end{closurestatus}
