\chapter{A Concrete Naming Certificate for $\RationalRealEmbeddingUp$}
\label{ch:concrete-instances-rational-real-embedding-namecert}
\origin{human}

Following Bishop and Bridges' construction of reals from rational Cauchy data, the $\RationalRealEmbeddingUp$ packet names the constant-rational route from the arithmetic source $\RatUp$ to the regular Cauchy and terminal real-name layers. It sits over the rational certificate of \autoref{ch:concrete-instances-rat-namecert}, the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is the finite source boundary for rational constants inside the L10 completion route; it does not quotient streams, select limits, assert host real equality, invoke countable choice, or prove ambient completeness of $\RealUp$.

\begin{definition}[Rational-real embedding carrier]
\label{def:rational-real-embedding-carrier}
A $\RationalRealEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
E=(Q,S,R,D,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\RatUp$ source row, containing the rational constant together with the finite arithmetic source data allowed to be read by the embedding packet.
\item $S$ is the constant $\StreamNameUp$ window row: each displayed window reads the same rational source $Q$ and contains no varying tail schedule.
\item $R$ is the $\RegSeqRatUp$ constant readback row, recording that every regular rational name coordinate is read back as the rational source from $Q$ through the windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the zero-tail and dyadic comparison budget used to certify that the constant readback satisfies every displayed regularity request.
\item $T$ is the $\RealUp$ seal row reached from $Q,S,R,D$, naming the terminal real-facing certificate for the rational constant.
\item $H$ records componentwise $\hsame$ transport for the rational source, constant windows, regular readback, dyadic tolerance ledger, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a rational-real embedding request through $Q,S,R,D,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RationalRealEmbeddingUp$, $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RationalRealEmbeddingUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through $Q,S,R,D,T,H,C,P,N$. It has no coordinate for quotient streams, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.RationalRealEmbeddingUp.RationalRealEmbeddingTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Rational-real embedding NameCert obligations]
\label{thm:rational-real-embedding-namecert-obligations}
For every accepted $\RationalRealEmbeddingUp$ carrier $E=(Q,S,R,D,T,H,C,P,N)$, the local $\NameCert_{\RationalRealEmbeddingUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the rational source, constant stream windows, regular rational constant readback, dyadic tolerance ledger, terminal real seal, transport, replay, provenance, and local naming rows;
\item rational-source admission, requiring every exported constant to pass through the displayed $\RatUp$ row $Q$;
\item constant-window admission, requiring every $\StreamNameUp$ window in $S$ to replay the same rational source and no independent tail schedule;
\item regular-readback admission, requiring $R$ to expose the constant rational name through the displayed windows in $S$;
\item tolerance admission, requiring $D$ to discharge the regularity requests by the zero-tail dyadic ledger attached to $Q,S,R$;
\item seal admission, requiring the $\RealUp$ row $T$ to be read only after $Q,S,R,D$ have been fixed;
\item non-escape, requiring $H,C,P,N$ to export no quotient-stream equality, selected limit, countable-choice selector, host real equality, trichotomy datum, ambient completeness theorem, Lean verification credential, or bridge credential.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:rational-real-embedding-carrier}. The accepted packet displays exactly the rational source, constant windows, regular readback, dyadic tolerance ledger, terminal real seal, and structural rows.

The rational-source and constant-window obligations are then forced by row order. A constant exported by the packet first reads $Q$, and every window in $S$ is attached to that same rational source rather than to a separate stream tail.

The regular-readback and tolerance obligations use the next two rows. The row $R$ reads the constant rational name through $S$, while $D$ supplies the dyadic zero-tail ledger that answers the finite regularity tests.

The terminal seal obligation is downstream. The $\RealUp$ row $T$ can be cited only after $Q,S,R,D$ are already displayed, so the real-facing name is a seal of the finite constant route rather than a selected host limit.

The remaining rows are structural. Componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row preserve and source the same displayed packet; none contains a quotient stream, selected limit, choice selector, host equality, trichotomy datum, ambient completeness theorem, Lean credential, or bridge credential.
\end{proof}

\begin{theorem}[Rational-real embedding real-seal factorization]
\label{thm:rational-real-embedding-real-seal-factorization}
Every $\RealUp$ seal exported by an accepted $\RationalRealEmbeddingUp$ carrier $E=(Q,S,R,D,T,H,C,P,N)$ factors through the finite route
$$
Q,S,R,D \longmapsto T
$$
before transport, replay, provenance, or local naming can be read. Consequently the embedding of a rational constant into the real-name layer is witnessed by a displayed constant StreamName route and a RegSeqRat readback, not by quotienting streams or selecting a limit.
\end{theorem}
\begin{proof}
Start with an exported real seal. The carrier has only one real-facing coordinate, namely $T$, and that row is listed after the rational source, constant-window, regular-readback, and dyadic-ledger rows.

The source row $Q$ fixes the rational constant. The stream row $S$ then opens only constant windows over $Q$, so no later step can introduce a variable Cauchy tail or an independent schedule.

The regular readback row $R$ reads those windows as a constant regular rational name. The dyadic ledger $D$ records the zero-tail tolerance facts needed by the displayed regularity requests.

Only after these four rows are fixed may $T$ be read as a $\RealUp$ seal. Transport, replay, provenance, and local naming preserve that same order, so the exported seal factors through $Q,S,R,D$ and never through a quotient stream or selected limit.
\end{proof}

\begin{theorem}[Rational-real embedding constant-window coherence]
\label{thm:rational-real-embedding-constant-window-coherence}
For every accepted $\RationalRealEmbeddingUp$ carrier $E=(Q,S,R,D,T,H,C,P,N)$, any two finite $\StreamNameUp$ window reads exposed by $S$ over inspected unary indices are classifier-equal through the same rational source row $Q$. The $\RegSeqRatUp$ readback row $R$, the $\DyadicRatCoreUp$ tolerance row $D$, and the terminal $\RealUp$ seal row $T$ may consume only that constant-window surface.
\end{theorem}
\begin{proof}
Project the accepted carrier. By the carrier definition, the row $S$ is the constant $\StreamNameUp$ window row attached to the rational source $Q$, and it contains no coordinate for a varying tail schedule.

Now compare two inspected unary-index windows in $S$. Each window reads the same displayed rational source row $Q$, so their classifier comparison is mediated by that source row rather than by an external stream representative.

Transport preserves the comparison componentwise through $H$. Replay through $C$ can only cite the displayed route $Q,S,R,D,T,H,P,N$, so it reuses the same constant-window surface instead of creating a second tail schedule.

The downstream rows are therefore constrained by source order. The readback row $R$ reads the constant windows already exposed by $S$, the tolerance row $D$ evaluates the zero-tail ledger attached to that readback, and the seal row $T$ is reached only after those rows have been fixed.
\end{proof}

\begin{theorem}[Rational-real embedding nonescape]
\label{thm:rational-real-embedding-nonescape}
Every rational-source, stream-window, regular-readback, dyadic-tolerance, or real-seal read of an accepted $\RationalRealEmbeddingUp$ carrier $E=(Q,S,R,D,T,H,C,P,N)$ is exhausted by the displayed rows $Q,S,R,D,T,H,C,P,N$. Thus the local $\NameCert_{\RationalRealEmbeddingUp}$ boundary exports only the rational source, constant StreamName windows, RegSeqRat constant readback, DyadicRatCore tolerance ledger, RealUp seal row, componentwise transport, continuation replay, provenance, and local naming data.

It exports no quotient-stream equality, selected limit, countable-choice selector, host real equality, trichotomy datum, ambient $\RealUp$ completeness theorem, Lean verification credential, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted carrier. The tuple $E=(Q,S,R,D,T,H,C,P,N)$ lists every coordinate admitted by the local $\NameCert_{\RationalRealEmbeddingUp}$ surface.

The analytic route is $Q,S,R,D,T$. It fixes a rational source, opens constant finite windows, reads them as a regular rational name, supplies the dyadic tolerance ledger, and then seals the result as a $\RealUp$ name.

The structural route is $H,C,P,N$. These rows transport, replay, source, and name the same displayed carrier; they do not add analytic coordinates or external equality principles.

Since no excluded object occurs as a coordinate or replay target, no read can escape to quotient-stream equality, selected limits, countable choice, host real equality, trichotomy, ambient Real completeness, Lean verification, or a bridge credential.
\end{proof}

\closureat{RationalRealEmbeddingUp}{seedStr}

\begin{closurestatus}{\RationalRealEmbeddingUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rational-real-embedding-carrier}, \autoref{thm:rational-real-embedding-namecert-obligations}, \autoref{thm:rational-real-embedding-real-seal-factorization}, \autoref{thm:rational-real-embedding-constant-window-coherence}, and \autoref{thm:rational-real-embedding-nonescape} seed the finite rational-constant embedding route from $\RatUp$ through constant $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance, and the terminal $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, rational-source admission, constant-window admission, regular-readback admission, dyadic-tolerance admission, real-seal factorization, transport stability, and non-escape proofs for BEDC.Derived.RationalRealEmbeddingUp.}
  \constructivestory{A $\RationalRealEmbeddingUp$ packet is generated from a RatUp source row, constant StreamName windows, RegSeqRat constant readback, a DyadicRatCore tolerance ledger, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
