\chapter{A Concrete Naming Certificate for $\RealityConstrainedModelAuditUp$}
\label{ch:concrete-instances-reality-constrained-model-audit-namecert}
\origin{ai}

The $\RealityConstrainedModelAuditUp$ interface realizes the physical model audit program of \autoref{sec:constructive-model-audit} as a finite BEDC naming certificate. It sits next to the finite stream and real-name surfaces of \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-real-namecert}: those chapters supply finite observation names and real-valued readback rows, while this chapter packages the physical audit rows that decide whether a model-facing fit claim may pass an acceptance gate.

\begin{definition}[Reality-constrained model-audit carrier]
\label{def:reality-constrained-model-audit-carrier}
A $\RealityConstrainedModelAuditUp$ carrier is a finite $\BHist$ packet
$$
A=(H,\Pi,O,M,C,T,L,F,S)
$$
whose displayed rows are as follows:
\begin{enumerate}
\item $H$ is the finite source-trace history for the audited physical system;
\item $\Pi$ is the observation bundle naming the finite queries through which the system is read;
\item $O$ is the observed-signature row extracted from $H$ under $\Pi$;
\item $M$ is the model-generated signature row declared by the candidate model;
\item $C$ is the classifier row comparing $O$ and $M$ at the declared physical-fit level;
\item $T$ is the approximation-tower row by which source traces, observations, and model signatures are related;
\item $L$ is the audit-ledger row recording provenance, hidden compression, translation, and idealization entries;
\item $F$ is the failure-surface row naming the finite defeating observations or signature mismatches that would invalidate the declared claim;
\item $S$ is the audit-strength row, ranging from seed-level model support through reproduced and bridged fit surfaces.
\end{enumerate}
The carrier is exactly this finite packet. It contains no unrecorded source row, no hidden compression step, no external oracle for model truth, and no physical-fit claim outside the displayed ledger.
\end{definition}

\begin{definition}[Reality-constrained model-audit classifier]
\label{def:reality-constrained-model-audit-classifier}
For accepted packets
$$
A=(H,\Pi,O,M,C,T,L,F,S)
\quad\hbox{and}\quad
A'=(H',\Pi',O',M',C',T',L',F',S'),
$$
the predicate $\mathsf{RealityConstrainedModelAuditClassifier}(A,A')$ holds when the component rows are related by displayed $\hsame$ transports, the observation bundle routes replay through the same finite source-trace schedule, the observed and model-generated signatures preserve the classifier comparison, the approximation tower and audit ledger transport componentwise, the failure-surface rows name the same defeating tests, and the declared strength comparison is preserved.

Thus classifier agreement is not raw equality of models. It is hsame-stable agreement of the source, observation, signature, classifier, tower, ledger, failure, and strength rows together with preservation of the declared physical-fit comparison.
\end{definition}

\begin{theorem}[Reality-constrained model-audit NameCert obligations]
\label{thm:reality-constrained-model-audit-namecert-obligations}
For the carrier of \autoref{def:reality-constrained-model-audit-carrier}, the local $\NameCert_{\RealityConstrainedModelAuditUp}$ surface consists of the following five obligation rows:
\begin{enumerate}
\item carrier admission: the accepted object is exactly $A=(H,\Pi,O,M,C,T,L,F,S)$;
\item classifier stability: every accepted comparison uses the classifier of \autoref{def:reality-constrained-model-audit-classifier};
\item signature exactness: the observed row $O$ and model-generated row $M$ are the only signatures licensed for the fit claim;
\item ledger exactness: every compression, translation, idealization, and hidden-content row used by the audit appears in $L$;
\item non-escape: a fit claim that depends on a row absent from $H,\Pi,O,M,C,T,L,F,S$ is outside the acceptance gate.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission projects the nine rows displayed in \autoref{def:reality-constrained-model-audit-carrier}. Each accepted read begins from the same finite packet, so no additional source trace or model-signature coordinate can be introduced later in the certificate.

Classifier stability follows by unpacking \autoref{def:reality-constrained-model-audit-classifier}. The transports compare the source, observation, signature, tower, ledger, failure, and strength rows componentwise and preserve the declared fit comparison.

The signature and ledger obligations are the distinguished projections of the same packet. Rows $O$ and $M$ carry the comparison surface, while $L$ records the compression, translation, idealization, and hidden-content material consumed by that comparison.

The non-escape clause is forced by the carrier inventory. Since the packet has no coordinate beyond $H,\Pi,O,M,C,T,L,F,S$, a claim depending on any unlisted row cannot be projected by the local naming certificate.
\end{proof}

\begin{theorem}[Reality-constrained model-audit ledger non-escape]
\label{thm:reality-constrained-model-audit-ledger-nonescape}
A model-audit packet with an unledgered compression row cannot pass the acceptance gate for any fit claim whose signature depends on that hidden row. The accepted route must expose the source trace, observation bundle, observed signature, model-generated signature, classifier, approximation tower, audit ledger, failure surface, and strength row before the fit claim is read.
\end{theorem}
\begin{proof}
Read the NameCert obligations of \autoref{thm:reality-constrained-model-audit-namecert-obligations}. Ledger exactness places every compression or translation row used by the fit comparison inside $L$.

If a fit claim depends on a hidden compression row not present in $L$, then the claim asks the acceptance gate to read a coordinate outside $A=(H,\Pi,O,M,C,T,L,F,S)$. The non-escape obligation excludes exactly that route.

Therefore the acceptance gate can pass only claims whose signature dependence is visible in the displayed ledger. The unledgered row remains outside the accepted packet.
\end{proof}

\begin{theorem}[Reality-constrained model-audit fit separation]
\label{thm:reality-constrained-model-audit-fit-separation}
Two accepted $\RealityConstrainedModelAuditUp$ packets may agree on source traces and observation bundles while remaining separated as physical audit certificates whenever their declared physical-fit comparison, failure surface, or strength row is not preserved by the classifier. This separation is visible at the certificate level and does not require a host-side judgment that either model is false.
\end{theorem}
\begin{proof}
Use the classifier definition. Agreement of $H$ and $\Pi$ supplies only the source and observation-bundle transports.

The same classifier also requires preservation of the observed and model-generated signatures, the physical-fit comparison, the tower, the ledger, the failure surface, and the strength row. If any of the comparison, failure, or strength rows is not preserved, the classifier relation fails even when the source rows agree.

The failure of classifier transport is an audit separation, not a truth judgment. It says that the two packets do not present the same licensed physical-fit certificate.
\end{proof}

\begin{theorem}[Reality-constrained model-audit signature exactness]
\label{thm:reality-constrained-model-audit-signature-exactness}
Every accepted $\RealityConstrainedModelAuditUp$ audit route for
$$
A=(H,\Pi,O,M,C,T,L,F,S)
$$
reads exactly the observed row $O$ and the model row $M$ extracted from the same source trace $H$ and observation bundle $\Pi$. No alternative observed signature, model signature, classifier input, approximation witness, ledger entry, failure row, or strength row can be substituted without leaving the accepted packet.
\end{theorem}
\begin{proof}
Start with carrier admission in \autoref{thm:reality-constrained-model-audit-namecert-obligations}. It identifies the accepted object with the nine displayed rows of \autoref{def:reality-constrained-model-audit-carrier}, so the audit route has no coordinate from which a second observed or model-generated signature can be read.

The classifier of \autoref{def:reality-constrained-model-audit-classifier} then binds the signature comparison to the same $H$ and $\Pi$ transports. Since classifier stability preserves the displayed comparison row $C$, any route using different signature inputs fails to be the same accepted classifier route.

Ledger non-escape in \autoref{thm:reality-constrained-model-audit-ledger-nonescape} excludes a hidden replacement through compression, translation, or idealization. The fit-separation theorem shows that a changed comparison row is an audit separation rather than another certificate for the same route.
\end{proof}

\begin{theorem}[Reality-constrained model-audit failure-surface exhaustion]
\label{thm:reality-constrained-model-audit-failure-surface-exhaustion}
For an accepted $\RealityConstrainedModelAuditUp$ fit claim on $A=(H,\Pi,O,M,C,T,L,F,S)$, every defeating observation and every signature mismatch used against the claim is named in the finite failure-surface row $F$. A defeat that requires an observation route or mismatch row absent from $F$ is outside the displayed audit certificate.
\end{theorem}
\begin{proof}
The NameCert obligation surface fixes $F$ as one of the carrier rows and makes non-escape part of the accepted audit. Thus a defeating test used by the certificate must be a projection from $A$, not an extra host-side objection added after acceptance.

Classifier stability requires the failure-surface rows of compared packets to name the same defeating tests. If a mismatch is not present in $F$, the classifier has no component on which to transport it as part of the accepted fit comparison.

Ledger non-escape also blocks hiding the missing defeat inside $L$. The ledger may expose provenance, compression, translation, and idealization rows, but it does not create an unlisted failure coordinate. Hence the finite row $F$ exhausts the defeating observations and signature mismatches licensed by the audit route.
\end{proof}

\begin{theorem}[Reality-constrained model-audit strength-row transport]
\label{thm:reality-constrained-model-audit-strength-row-transport}
Whenever $\mathsf{RealityConstrainedModelAuditClassifier}(A,A')$ holds for
$$
A=(H,\Pi,O,M,C,T,L,F,S)
\quad\hbox{and}\quad
A'=(H',\Pi',O',M',C',T',L',F',S'),
$$
the classifier transports the audit-strength row $S$ to $S'$. Therefore classifier agreement cannot upgrade the evidential grade of a fit claim unless the transported strength row already presents that grade.
\end{theorem}
\begin{proof}
Unpack the classifier definition. Alongside the source, observation, signature, tower, ledger, and failure rows, it includes preservation of the declared strength comparison.

The NameCert obligations and ledger non-escape prevent the strength grade from being imported through an unrecorded coordinate. The accepted packet has only the displayed row $S$ for audit strength, and any grade used by the fit claim must be read from that row.

Finally apply \autoref{thm:reality-constrained-model-audit-fit-separation}. If strength is not preserved, the packets are separated as physical audit certificates even when their source and observation rows agree. Thus transported classifier agreement carries $S$; it does not manufacture a stronger evidential grade.
\end{proof}

The later Lean file \texttt{lean4/BEDC/Derived/RealityConstrainedModelAuditUp/TasteGate.lean} must provide \texttt{Nontrivial RealityConstrainedModelAuditUp} with two distinct audit packets and \texttt{FieldFaithful RealityConstrainedModelAuditUp} by \texttt{.mk} projections from $H,\Pi,O,M,C,T,L,F,S$ and injection on the displayed field surface.

\falsifiablePrediction{A model-audit packet with an unledgered compression row cannot pass the acceptance gate for any fit claim whose signature depends on the hidden row.}

\independenceWitness{Compare largemodelauditchannel, largemodelcorpussupply, physicalfit, finitewindowenvelope, and streamname: those siblings supply channel, corpus, window, and stream rows, but none carries the ten-field physical audit certificate with failure-surface and strength coordinates, so no bijection preserves the obligation rows.}

\closureat{RealityConstrainedModelAuditUp}{scopedStr}[BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment]
\closureat{RealityConstrainedModelAuditUp}{publicStr}[BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment]
\closureat{RealityConstrainedModelAuditUp}{bridgedStr}[BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment]
\closureat{RealityConstrainedModelAuditUp}{matureStr}[BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\RealityConstrainedModelAuditUp}
  \constructivestory{A $\RealityConstrainedModelAuditUp$ packet is generated from a finite source-trace history, observation bundle, observed signature, model-generated signature, classifier comparison, approximation tower, audit ledger, failure surface, and audit-strength row.}
  \leanchecked{BEDC.Derived.RealityConstrainedModelAuditUp.taste\_gate}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{def:reality-constrained-model-audit-carrier}, \autoref{def:reality-constrained-model-audit-classifier}, \autoref{thm:reality-constrained-model-audit-namecert-obligations}, \autoref{thm:reality-constrained-model-audit-ledger-nonescape}, \autoref{thm:reality-constrained-model-audit-fit-separation}, \autoref{thm:reality-constrained-model-audit-signature-exactness}, \autoref{thm:reality-constrained-model-audit-failure-surface-exhaustion}, and \autoref{thm:reality-constrained-model-audit-strength-row-transport} bind the finite carrier, classifier, NameCert obligations, ledger non-escape, fit separation, and exact audit rows for signatures, failures, and strength.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.RealityConstrainedModelAuditUp.RealityConstrainedModelAuditTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not prove host-level model truth, unbounded physical validation, continuous experimental adequacy, hidden-source recovery, axiom-clean audit, or bridge checking for $\RealityConstrainedModelAuditUp$.}
  \upgradepath{No further paper-side theory upgrade is pending; bridge checking remains a separate verification-axis matter.}
\end{closurestatus}
