\chapter{A Concrete Naming Certificate for $\NatRealEmbeddingUp$}
\label{ch:concrete-instances-nat-real-embedding-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\NatRealEmbeddingUp$ packet records the finite route by which a displayed $\NatUp$ unary source row becomes a $\RealUp$ name through an exact rational constant. It sits over the natural-number certificate of \autoref{ch:concrete-instances-nat-namecert}, the rational source surface of \autoref{ch:concrete-instances-rat-namecert}, the rational-to-real constant route of \autoref{ch:concrete-instances-rational-real-embedding-namecert}, the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic zero-tail tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet routes a displayed $\NatUp$ unary source row into a rational constant row, constant $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ zero-tail tolerance, and the terminal $\RealUp$ seal.

\begin{definition}[Nat-real embedding carrier]
\label{def:nat-real-embedding-carrier}
A $\NatRealEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
K=(n,q,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $n$ is the $\NatUp$ unary source row naming the natural-number input.
\item $q$ is the $\RatUp$ rational constant row obtained by reading $n$ as $n/1$.
\item $S$ is the constant $\StreamNameUp$ schedule whose admitted finite windows all read the same rational row $q$.
\item $R$ is the $\RegSeqRatUp$ readback row for the constant schedule $S$.
\item $D$ is the $\DyadicRatCoreUp$ zero-tail tolerance ledger attached to the finite reads of $R$.
\item $E$ is the terminal $\RealUp$ seal reached only after $n,q,S,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the natural source, rational constant row, constant stream schedule, regular readback, dyadic tolerance ledger, real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a nat-real embedding request through $n,q,S,R,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\NatRealEmbeddingUp$, $\NatUp$, $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NatRealEmbeddingUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $n,q,S,R,D,E,H,C,P,N$. It has no coordinate for quotient streams, selected limits, host $\NatUp$ equality, host real equality, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Nat-real embedding NameCert obligations]
\label{thm:nat-real-embedding-namecert-obligations}
For every accepted $\NatRealEmbeddingUp$ carrier $K=(n,q,S,R,D,E,H,C,P,N)$, the local $\NameCert_{\NatRealEmbeddingUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the natural source, rational constant row, constant stream windows, regular rational readback, dyadic zero-tail tolerance ledger, terminal real seal, transport, replay, provenance, and local naming rows;
\item source admission, requiring every exported constant to pass through the displayed $\NatUp$ row $n$ before the rational row $q$ is read;
\item constant-window exactness, requiring every admitted $\StreamNameUp$ window in $S$ to replay the same rational constant row $q$ and no independent tail schedule;
\item regular-readback admission, requiring $R$ to expose the constant rational name only through the displayed windows in $S$;
\item dyadic zero-tail tolerance, requiring $D$ to answer finite regularity requests by the zero-tail ledger attached to $q,S,R$;
\item Real seal nonescape, requiring $E$ to be downstream of $n,q,S,R,D$ and to expose no quotient stream, selected limit, host $\NatUp$ equality, host real equality, trichotomy, countable-choice selector, ambient completeness theorem, Lean verification credential, or bridge credential;
\item ledger exhaustion, requiring $H,C,P,N$ to transport, replay, source, and name exactly the same finite nat-real embedding packet.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.NatRealEmbeddingUp.NatRealEmbeddingTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:nat-real-embedding-carrier}. The accepted packet displays exactly the natural source, rational constant row, constant windows, regular readback, dyadic zero-tail ledger, terminal real seal, and structural rows.

Source admission and constant-window exactness are forced by row order. A real-facing constant first reads $n$, then the rational row $q$, and every window in $S$ is attached to that same rational row rather than to a separate stream seed.

The regular-readback and dyadic-tolerance rows are downstream. The row $R$ reads the constant windows as a regular rational name, while $D$ supplies the zero-tail tolerance ledger for finite regularity tests.

The real seal and ledger rows cannot add external principles. The row $E$ is reached only after $n,q,S,R,D$, and the rows $H,C,P,N$ preserve, replay, source, and name the same displayed packet. Since none of the excluded objects appears as a coordinate, the listed rows exhaust the local surface.
\end{proof}

\begin{theorem}[Nat-real embedding Real seal factorization]
\label{thm:nat-real-embedding-real-seal-factorization}
Every $\RealUp$ seal exported by an accepted $\NatRealEmbeddingUp$ carrier $K=(n,q,S,R,D,E,H,C,P,N)$ factors through the finite route
$$
n,q,S,R,D \longmapsto E
$$
before transport, replay, provenance, or local naming can be read. Consequently the embedding of a natural-number constant into the real-name layer is witnessed by the displayed $\NatUp$ source, rational constant row, constant $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ zero-tail tolerance ledger, not by quotienting streams or selecting a limit.
\end{theorem}
\begin{proof}
Start with an exported real seal. The carrier has only one real-facing coordinate, namely $E$, and that row is listed after the natural source, rational constant, constant-window, regular-readback, and dyadic-ledger rows.

The source row $n$ fixes the natural-number input. The rational row $q$ records the exact constant $n/1$, and the stream row $S$ opens only finite windows over that same rational row.

The regular readback row $R$ reads those windows as a constant regular rational name. The dyadic ledger $D$ records the zero-tail tolerance facts needed by the displayed regularity requests.

Only after these five rows are fixed may $E$ be read as a $\RealUp$ seal. Transport, replay, provenance, and local naming preserve that same order, so the exported seal factors through $n,q,S,R,D$ before any structural row is consulted.
\end{proof}

\closureat{NatRealEmbeddingUp}{seedStr}

\begin{closurestatus}{\NatRealEmbeddingUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nat-real-embedding-carrier}, \autoref{thm:nat-real-embedding-namecert-obligations}, and \autoref{thm:nat-real-embedding-real-seal-factorization} seed the finite natural-constant embedding route from $\NatUp$ through a rational constant row, constant $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ zero-tail tolerance, and the terminal $\RealUp$ seal.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.NatRealEmbeddingUp.NatRealEmbeddingTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, host $\NatUp$ equality, host real equality, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source admission, constant-window exactness, regular-readback admission, dyadic zero-tail tolerance, Real seal nonescape, ledger exhaustion, and factorization proofs for BEDC.Derived.NatRealEmbeddingUp.}
  \constructivestory{A $\NatRealEmbeddingUp$ packet is generated from a NatUp unary source row, RatUp rational constant row, constant StreamName windows, RegSeqRat constant readback, DyadicRatCore zero-tail tolerance ledger, RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert row.}
\end{closurestatus}
