\chapter{A Concrete Naming Certificate for $\CompactIntervalLocatorUp$}
\label{ch:concrete-instances-compact-interval-locator-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CompactIntervalLocatorUp$ packet records finite locator data for a compact real interval through existing $\LocatedRealIntervalUp$, $\RealLocatorUp$, $\LocatednessModulusUp$, $\DyadicIntervalArithmeticUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. The chapter binds the interval surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, the comparison service of \autoref{ch:concrete-instances-real-locator-namecert}, and the locatedness budget of \autoref{ch:concrete-instances-locatedness-modulus-namecert} as one finite consumer packet. It gives Real and Completion routes a compact-interval locator surface; it is not open-cover compactness, endpoint selection, real-order trichotomy, quotient-stream equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Compact interval locator carrier]
\label{def:compact-interval-locator-carrier}
A $\CompactIntervalLocatorUp$ carrier is a finite $\BHist$ packet
$$
K=(I,\Lambda,M,D,S,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\LocatedRealIntervalUp$ source interval row, exposing the lower and upper $\RealUp$ endpoint names, radius budget, endpoint compatibility, locator reads, and locatedness services already admitted by the interval packet.
\item $\Lambda$ is the $\RealLocatorUp$ comparison row used for rational probes against the displayed interval boundary.
\item $M$ is the $\LocatednessModulusUp$ row that turns each positive tolerance request into finite endpoint windows, rational cells, dyadic refinements, and real-name readbacks.
\item $D$ is the $\DyadicIntervalArithmeticUp$ ledger for endpoint enclosure, interval refinement, containment comparison, and outward dyadic slack.
\item $S$ is the $\StreamNameUp$ finite-window row opened by the Real and Completion consumer request.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same endpoint and tolerance windows.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance ledger recording the requested positive dyadic scale and the rational comparison cells inspected by the locator.
\item $H$ records componentwise $\hsame$ transport for the located interval, locator, modulus, dyadic interval ledger, stream windows, regular readback, dyadic tolerance ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact-interval location request through $I,\Lambda,M,D,S,R,Q,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CompactIntervalLocatorUp$, $\LocatedRealIntervalUp$, $\RealLocatorUp$, $\LocatednessModulusUp$, $\DyadicIntervalArithmeticUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactIntervalLocatorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $I,\Lambda,M,D,S,R,Q,H,C,P,N$. It has no coordinate for open-cover compactness, selected endpoints, host closed-interval equality, trichotomy, quotient stream equality, countable choice, ambient Real completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Compact interval locator NameCert obligations]
\label{thm:compact-interval-locator-namecert-obligations}
For every accepted $\CompactIntervalLocatorUp$ carrier
$$
K=(I,\Lambda,M,D,S,R,Q,H,C,P,N),
$$
the local $\NameCert_{\CompactIntervalLocatorUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located interval row, real locator row, locatedness modulus row, dyadic interval arithmetic ledger, StreamName window row, RegSeqRat readback row, DyadicRatCore tolerance ledger, transport, replay, provenance, and local naming;
\item interval-source exactness, requiring every endpoint, radius, containment, and boundary request to pass through the displayed $\LocatedRealIntervalUp$ row $I$;
\item locator-modulus compatibility, requiring $\Lambda$ and $M$ to answer rational probes and tolerance requests through the same finite endpoint windows, dyadic cells, and real-name readback route;
\item dyadic ledger stability, requiring $D$ and $Q$ to store only displayed dyadic interval arithmetic, positive scales, and rational comparison cells;
\item consumer-window exhaustion, requiring $S$ and $R$ to expose finite windows and regular rational readback before any $\RealUp$ or Completion-facing seal is read;
\item nonescape, excluding open-cover compactness, selected endpoints, host interval equality, real-order trichotomy, quotient stream equality, countable choice, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
No compact interval locator obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-interval-locator-carrier}. The accepted packet displays exactly one located interval source, one locator row, one locatedness modulus, one dyadic interval ledger, one finite stream-window row, one regular readback row, one dyadic tolerance ledger, and the structural rows.

Interval-source exactness is forced by $I$. Endpoint, radius, containment, separation, and refinement requests have no second interval coordinate, so every such read begins with the displayed $\LocatedRealIntervalUp$ carrier.

Locator-modulus compatibility is the pair $\Lambda,M$. The locator row answers rational boundary probes, while the modulus row converts tolerance requests into the same finite endpoint windows, rational cells, dyadic refinements, and real-name readbacks.

Dyadic and consumer-window stability are supplied by $D,Q,S,R$. The dyadic rows name only displayed interval arithmetic, positive scales, and rational comparison cells; the window rows expose only finite StreamName windows and RegSeqRat readback.

The remaining rows $H,C,P,N$ transport, replay, source, and name the same packet. Since the excluded compactness, endpoint-selection, order, quotient, choice, and ambient completeness data are absent from the carrier inventory, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Compact interval locator Real route]
\label{thm:compact-interval-locator-real-route}
Every $\RealUp$ or Completion-facing read of an accepted $\CompactIntervalLocatorUp$ carrier factors through the finite route
$$
I \longmapsto \Lambda,M,D,Q \longmapsto S,R \longmapsto H,C,P,N .
$$
The read may inspect the located real interval, locator decisions, locatedness budgets, dyadic interval arithmetic, dyadic tolerance cells, finite stream windows, regular rational readback, transport, replay, provenance, and local naming. It may not replace that route by open-cover compactness, selected endpoints, host interval equality, trichotomy, quotient stream equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(I,\Lambda,M,D,S,R,Q,H,C,P,N)$. The only source interval coordinate is $I$, so every Real or Completion-facing request first reads the located interval row with its endpoint, radius, locator, and locatedness boundary.

The computational route is then forced through $\Lambda,M,D,Q$. These rows provide the finite locator decisions, tolerance-to-window budget, dyadic interval arithmetic, and dyadic rational comparison cells for the same displayed interval.

The consumer-facing observation is finite. The request opens the StreamName window $S$ and reads it through the RegSeqRat row $R$ before any Real-facing seal can be consumed.

Finally $H,C,P,N$ preserve, replay, source, and name the displayed route. None of these rows contains open-cover compactness, selected endpoint functionals, host interval equality, trichotomy, quotient stream equality, countable choice, or ambient $\RealUp$ completeness, so every accepted read remains inside the stated route.
\end{proof}

\falsifiablePrediction{Every $\CompactIntervalLocatorUp$ read factors through one $\LocatedRealIntervalUp$ source row, one $\RealLocatorUp$ comparison row, one $\LocatednessModulusUp$ tolerance row, one $\DyadicIntervalArithmeticUp$ ledger, one $\StreamNameUp$ finite-window row, one $\RegSeqRatUp$ readback row, one $\DyadicRatCoreUp$ tolerance ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{located-real-interval, real-locator, locatedness-modulus: $\CompactIntervalLocatorUp$ is not bijective to any listed sibling because it jointly carries source interval data, boundary locator decisions, tolerance-to-window budgets, dyadic interval arithmetic, finite observation windows, regular rational readback, and a Real or Completion-facing nonescape boundary as one local NameCert packet.}

\closureat{CompactIntervalLocatorUp}{seedStr}

\begin{closurestatus}{\CompactIntervalLocatorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-interval-locator-carrier}, \autoref{thm:compact-interval-locator-namecert-obligations}, and \autoref{thm:compact-interval-locator-real-route} seed the finite compact-interval locator route over located real intervals, real locators, locatedness moduli, dyadic interval arithmetic, stream windows, regular rational readback, and dyadic tolerance ledgers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected endpoints, host interval equality, real-order trichotomy, quotient stream equality, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, interval-source exactness, locator-modulus compatibility, dyadic ledger stability, consumer-window exhaustion, and Real-route nonescape proofs for BEDC.Derived.CompactIntervalLocatorUp.}
  \constructivestory{A $\CompactIntervalLocatorUp$ packet is generated from a LocatedRealIntervalUp row, a RealLocatorUp comparison row, a LocatednessModulusUp tolerance row, DyadicIntervalArithmeticUp rows, StreamNameUp windows, RegSeqRatUp readbacks, a DyadicRatCoreUp tolerance ledger, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
