\chapter{A Concrete Naming Certificate for $\RegularCauchyCancellationUp$}
\label{ch:concrete-instances-regular-cauchy-cancellation-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyCancellationUp$ packet records the finite cancellation boundary for displayed regular rational Cauchy names. It ties the pointwise sum route of \autoref{ch:concrete-instances-regularcauchysum-namecert}, the difference route of \autoref{ch:concrete-instances-regularcauchydifference-namecert}, the zero route of \autoref{ch:concrete-instances-regularcauchyzero-namecert}, the finite precision ledger of \autoref{ch:concrete-instances-finiteerrorbudget-namecert}, the regular source rows of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert} into one inspectable packet. The packet supplies a bounded route for cancelling a shared displayed summand before any $\RealUp$ consumer reads the result; it is not a completed-real additive group law, quotient stream equality, selected limits, trichotomy, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy cancellation carrier]
\label{def:regular-cauchy-cancellation-carrier}
A $\RegularCauchyCancellationUp$ carrier is a finite $\BHist$ packet
$$
K=(X,Y,Z,S_X,S_Y,D,B,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X,Y,Z$ are the three $\RegSeqRatUp$ source rows, with $Z$ the shared summand offered to both sum routes.
\item $S_X$ is the $\RegularCauchySumUp$ route for the displayed sum $X+Z$.
\item $S_Y$ is the $\RegularCauchySumUp$ route for the displayed sum $Y+Z$.
\item $D$ is the $\RegularCauchyDifferenceUp$ route comparing the two displayed sums and exposing the difference readback only through finite source windows, dyadic endpoint rows, and regular readback data.
\item $B$ is the $\FiniteErrorBudgetUp$ ledger that accounts for the two sum budgets, the difference budget, and the cancellation tolerance requested by a downstream consumer.
\item $Q$ is the $\RegularCauchyZeroUp$ boundary row used to identify the shared $Z-Z$ contribution as the displayed zero route, with any $\RegularCauchyNegationUp$ read confined to the sibling difference packet.
\item $R$ is the resulting $\RegSeqRatUp$ readback row for the finite cancellation route from $(X+Z)-(Y+Z)$ to $X-Y$.
\item $E$ is the $\RealUp$ seal row reached only after $S_X,S_Y,D,B,Q,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source rows, two sum routes, difference route, budget ledger, zero boundary, readback, seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a cancellation-facing precision request through $X,Y,Z,S_X,S_Y,D,B,Q,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyCancellationUp$, $\RegularCauchySumUp$, $\RegularCauchyDifferenceUp$, $\RegularCauchyZeroUp$, $\RegularCauchyNegationUp$, $\FiniteErrorBudgetUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyCancellationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,Z,S_X,S_Y,D,B,Q,R,E,H,C,P,N$. The carrier has no coordinate for completed-real additive group laws, quotient stream equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy cancellation NameCert obligation surface]
\label{thm:regular-cauchy-cancellation-namecert-obligations}
For every accepted $\RegularCauchyCancellationUp$ carrier
$$
K=(X,Y,Z,S_X,S_Y,D,B,Q,R,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyCancellationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the three $\RegSeqRatUp$ source rows, two $\RegularCauchySumUp$ routes, the $\RegularCauchyDifferenceUp$ comparison route, the $\FiniteErrorBudgetUp$ ledger, the zero boundary row, the readback row, and the structural rows;
\item sum exactness, requiring $S_X$ and $S_Y$ to expose the two displayed sums only through aligned $\StreamNameUp$ windows, $\DyadicRatCoreUp$ endpoint rows, and their own finite error ledgers;
\item difference exactness, requiring $D$ to compare the displayed sums through the sibling $\RegularCauchyDifferenceUp$ route before any cancellation readback is available;
\item zero-boundary exactness, requiring $Q$ to display the shared $Z-Z$ contribution through $\RegularCauchyZeroUp$ rather than through host real algebra;
\item budget exactness, requiring $B$ to account for the two sum budgets, the difference budget, and the cancellation tolerance before $R$ is consumed;
\item Real seal nonescape, requiring $E$ to be downstream of $R$ and to expose no completed-real additive group law, quotient stream equality, selected limit, trichotomy, countable choice, ambient completeness, Lean verification, or bridge row;
\item componentwise transport, replay, provenance, and local naming, requiring $H,C,P,N$ to preserve exactly the same finite cancellation packet.
\end{enumerate}
No cancellation obligation is stored outside these rows.
\end{theorem}

\begin{theorem}[Regular Cauchy left cancellation finite route]
\label{thm:regular-cauchy-cancellation-left-route}
Let $K=(X,Y,Z,S_X,S_Y,D,B,Q,R,E,H,C,P,N)$ be an accepted $\RegularCauchyCancellationUp$ carrier. Every consumer that reads the cancellation of the shared left-hand summand factors through the finite route
$$
X,Y,Z \longmapsto S_X,S_Y \longmapsto D,B,Q \longmapsto R,E,H,C,P,N .
$$
The consumer first reads the three source $\RegSeqRatUp$ rows and the two displayed sum routes, then the difference route between those sums, the finite budget ledger, and the zero boundary for the shared $Z-Z$ contribution, and only then obtains the regular readback and $\RealUp$ seal. The route exports no completed-real additive group law, quotient stream equality, selected limit, trichotomy witness, countable-choice selector, or ambient completeness principle.
\end{theorem}

\begin{theorem}[Regular Cauchy cancellation Real seal nonescape]
\label{thm:regular-cauchy-cancellation-real-seal-nonescape}
Every $\RealUp$ consumer of an accepted $\RegularCauchyCancellationUp$ carrier reaches the seal row $E$ only after the $\RegSeqRatUp$ readback $R$ has been assembled from the two $\RegularCauchySumUp$ routes, the $\RegularCauchyDifferenceUp$ route, the $\RegularCauchyZeroUp$ boundary row, and the $\FiniteErrorBudgetUp$ ledger. The real-facing boundary exposes the finite source rows, sum routes, difference route, zero route, budget ledger, readback, componentwise transport, continuation replay, provenance, and local naming. It exposes no completed-real additive group law, quotient stream equality, selected limit, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or public bridge row.
\end{theorem}

\closureat{RegularCauchyCancellationUp}{seedStr}

\begin{closurestatus}{\RegularCauchyCancellationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-cancellation-carrier}, \autoref{thm:regular-cauchy-cancellation-namecert-obligations}, \autoref{thm:regular-cauchy-cancellation-left-route}, and \autoref{thm:regular-cauchy-cancellation-real-seal-nonescape} seed the finite cancellation boundary through three $\RegSeqRatUp$ source rows, two sum routes, one difference route, one zero boundary row, one finite budget ledger, a regular readback, and a $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim completed-real additive group laws, quotient stream equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, sum exactness, difference exactness, zero-boundary exactness, budget exactness, Real seal nonescape, componentwise transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyCancellationUp.}
  \constructivestory{A $\RegularCauchyCancellationUp$ packet is generated from three $\RegSeqRatUp$ source rows, two $\RegularCauchySumUp$ routes, one $\RegularCauchyDifferenceUp$ route, one $\RegularCauchyZeroUp$ boundary row, one $\FiniteErrorBudgetUp$ ledger, a $\RegSeqRatUp$ readback, a $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
