\chapter{A Concrete Naming Certificate for $\SecondCountableUp$}
\label{ch:concrete-instances-second-countable-namecert}
\origin{human}

Following Bourbaki and Kelley on general topology, the $\SecondCountableUp$ packet records a countable-base interface as finite BEDC rows. It sits over the metric source surface of \autoref{ch:concrete-instances-metric-namecert}, the generated-open classifier of \autoref{ch:concrete-instances-topology-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic precision ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only the displayed base enumeration, local basis reads, refinement rows, and transport ledgers; it does not identify host sets, assert open-cover compactness, select a basis by choice, or import ambient $\RealUp$ completeness.

\begin{definition}[Second-countable carrier]
\label{def:second-countable-carrier}
A $\SecondCountableUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,T,M,B,D,S,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the point or source carrier row whose visible histories supply the only points read by the packet.
\item $T$ is the $\TopologyUp$ open-set classifier row, recording generated-open membership only through displayed BEDC histories.
\item $M$ is the $\MetricUp$ metric-ball witness row when the packet is metric-presented; if no metric row is present, $M$ is the explicit empty witness row.
\item $B$ is the displayed countable-base enumeration row, recording finite index windows and the basic-open cells exposed at those windows.
\item $D$ is the dyadic radius and precision ledger over $\DyadicRatCoreUp$ used by metric-ball and boundary reads.
\item $S$ is the $\StreamNameUp$ row for finite inspection windows of the base enumeration and consumer probes.
\item $R$ is the $\RealUp$ boundary and seal row used by radius, completion-facing, or real-valued classifier reads.
\item $H$ stores componentwise $\hsame$ transport for the source, topology classifier, metric witness, base enumeration, dyadic ledger, stream windows, real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a point or source read through the base enumeration, local basis test, refinement row, classifier transport, precision ledger, stream window, real seal, provenance, and local name.
\item $P$ is the $\Pkg$ provenance row over $\SecondCountableUp$, $\MetricUp$, $\TopologyUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SecondCountableUp}$ row.
\end{enumerate}
The carrier exposes no host set of opens, no selected countable basis, no countable-choice witness, no open-cover compactness proof, no Lindelof theorem, and no $\RealUp$ completeness field.
\end{definition}
\leanchecked{BEDC.Derived.SecondCountableUp.SecondCountableTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Second-countable NameCert obligations]
\label{thm:second-countable-namecert-obligations}
For an accepted $\SecondCountableUp$ carrier
$$
Q=(X,T,M,B,D,S,R,H,C,P,N),
$$
the local $\NameCert_{\SecondCountableUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the point or source row, topology classifier, optional metric-ball witness, displayed base enumeration, dyadic ledger, stream windows, real seal, transport, replay, provenance, and local name;
\item local-basis coverage, requiring every accepted point-window and open-classifier read to meet a displayed basic cell from $B$ through the same source row $X$ and topology row $T$;
\item basis refinement closure, requiring any two displayed basic cells accepted at a common point-window to refine through another displayed basic cell indexed by the same enumeration row $B$;
\item topology and metric classifier transport, requiring every open-set or metric-ball read to pass through $T$ and, when present, $M$ before it is exported to a consumer;
\item ledger nonescape, requiring every dyadic radius, stream-window, real-boundary, transport, replay, provenance, and local-naming read to remain inside the rows $D,S,R,H,C,P,N$.
\end{enumerate}
No second-countability obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.SecondCountableUp.SecondCountableCarrier\_namecert\_obligations}
\begin{proof}
Carrier admission is projection from \autoref{def:second-countable-carrier}. The accepted packet displays exactly one source row, topology classifier, metric witness slot, base enumeration, dyadic ledger, stream-window row, real-seal row, and structural rows.

Local-basis coverage is read from $X,T,B$. A consumer opens a point or source window in $X$, reads the generated-open classifier in $T$, and receives only a displayed basic cell from $B$ that is witnessed at the same finite window.

Basis refinement closure is also internal to $B$. When two displayed basic cells are accepted at a common point-window, the refinement row is another finite base-enumeration entry, not a host intersection or a choice-selected neighborhood.

Topology and metric classifier transport are forced by $T$ and $M$. The topology row supplies the open-set classifier, while the metric witness row supplies the ball route when the presentation has metric data; a non-metric packet exposes only the explicit empty metric slot.

Finally $D,S,R,H,C,P,N$ keep the read inside the finite ledger. Dyadic precision, stream windows, real boundary reads, componentwise transport, replay, provenance, and local naming are all packet fields, so no open-cover compactness theorem, Lindelof theorem, host basis, countable-choice witness, or $\RealUp$ completeness field can be exported.
\end{proof}

\begin{theorem}[Second-countable metric-base handoff]
\label{thm:second-countable-metric-base-handoff}
Every metric or topology consumer read of an accepted $\SecondCountableUp$ packet factors through the displayed route
$$
\MetricUp,\TopologyUp,\DyadicRatCoreUp,\StreamNameUp,\RealUp
$$
before any open-set or completion-facing read is accepted. A metric-presented packet first reads the $\MetricUp$ ball witness and dyadic radius ledger, then the $\StreamNameUp$ inspection window, then the $\TopologyUp$ generated-open classifier, and finally any $\RealUp$ boundary seal needed by a completion-facing consumer. A non-metric packet uses the same topology, stream, dyadic, and real-boundary rows while keeping the metric witness row empty.
\end{theorem}
\leanchecked{BEDC.Derived.SecondCountableUp.SecondCountableCarrier\_metric\_base\_handoff}
\begin{proof}
Start with the packet $Q=(X,T,M,B,D,S,R,H,C,P,N)$. A topology consumer has no open-set coordinate except $T$, so every open read begins with the displayed source row $X$, the topology classifier $T$, and the base enumeration row $B$.

If the consumer asks for a metric-ball presentation, the row $M$ is the only metric witness. Its radius and precision reads must pass through the dyadic ledger $D$ before the basic-open cell in $B$ is accepted.

The stream row $S$ names the finite inspection windows for the enumeration and consumer probes. It prevents the read from becoming a host sequence of basic opens or a selected countable basis.

The real boundary row $R$ is the only endpoint-facing seal. Completion-facing consumers therefore see the route through $M,D,S,T,B,R$ before any real-valued or completion-facing read is exported.

The structural rows $H,C,P,N$ transport, replay, source, and name the same route. Since the packet has no host-set equality coordinate, open-cover compactness witness, countable-choice field, or $\RealUp$ completeness field, the handoff stays inside the stated BEDC rows.
\end{proof}

\closureat{SecondCountableUp}{seedStr}

\begin{closurestatus}{\SecondCountableUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:second-countable-carrier}, \autoref{thm:second-countable-namecert-obligations}, and \autoref{thm:second-countable-metric-base-handoff} seed the finite countable-base interface over displayed source rows, topology classifiers, optional metric-ball witnesses, dyadic precision ledgers, stream windows, real seals, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.SecondCountableUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, Lindelof theorems, selected bases as host sets, countable choice, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, local-basis coverage, basis refinement, metric-base handoff, transport, replay, provenance, and local naming for BEDC.Derived.SecondCountableUp.}
  \constructivestory{A $\SecondCountableUp$ packet is generated from one point or source carrier row, one Topology classifier row, an optional Metric ball witness row, one displayed countable-base enumeration row, one DyadicRatCore precision ledger, one StreamName finite-inspection row, one Real boundary row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
