\chapter{A Concrete Naming Certificate for $\RolleTheoremUp$}
\label{ch:concrete-instances-rolle-theorem-namecert}
\origin{human}

Following Rolle and the Bishop--Bridges reading of constructive analysis, the $\RolleTheoremUp$ packet records the finite NameCert boundary behind the familiar stationary-point theorem without turning it into an ambient completeness principle. Its source rows are the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}, the pointwise continuity and modulus rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the derivative quotient route of \autoref{ch:concrete-instances-derivative-namecert}, the sign-change and bisection ledger of \autoref{ch:concrete-instances-intermediatevalue-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The chapter names the theorem-facing finite interface only: endpoint equality, interval localization, continuity, derivative inspection, rational readback, dyadic budgets, and a displayed zero-derivative handoff remain visible rows.

\begin{definition}[Rolle theorem carrier]
\label{def:rolle-theorem-carrier}
A $\RolleTheoremUp$ carrier is a finite $\BHist$ packet
$$
T=(A,B,E,F,Q,D,I,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A,B$ are the two endpoint real-name rows, read through the $\RealUp$ surface and retained with their regular rational readbacks.
\item $E$ is the endpoint-equality row, recording classifier equality of the two endpoint value seals rather than host equality of completed reals.
\item $F$ is the $\ContinuousMapUp$ row naming the displayed real-valued map over the located interval cells.
\item $Q$ is the $\RegSeqRatUp$ readback row for the finite endpoint and interior value inspections consumed by the theorem route.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger that bounds the inspected rational windows and derivative quotients.
\item $I$ is the $\IntermediateValueUp$ handoff row that supplies the finite bisection-facing sign and location ledger used to isolate the stationary witness.
\item $Z$ is the $\DerivativeUp$ zero-handoff row, exposing a displayed derivative quotient whose terminal seal is the $\RealUp$ zero seal.
\item $H$ records componentwise $\hsame$ transport for endpoint names, endpoint equality, map data, rational readbacks, dyadic tolerances, intermediate-value handoff, derivative quotient, zero seal, replay rows, provenance rows, and local naming rows.
\item $C$ records displayed $\Cont$ replay from endpoint reads to map windows, from rational readbacks to dyadic tolerance checks, from the intermediate-value ledger to the derivative-zero handoff, and from the derivative quotient to the terminal real-name zero seal.
\item $P$ is the $\Pkg$ provenance over $\RolleTheoremUp$, $\RealUp$, $\ContinuousMapUp$, $\DerivativeUp$, $\IntermediateValueUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RolleTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted theorem packets only through these rows. It has no coordinate for ambient $\RealUp$ completeness, trichotomy of real numbers, a selected root, host differentiability, quotient real equality, open-cover compactness, or a standard bridge.
\end{definition}
\leanchecked{BEDC.Derived.RolleTheoremUp.RolleTheoremTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Rolle theorem NameCert obligations]
\label{thm:rolle-theorem-namecert-obligations}
For every accepted $\RolleTheoremUp$ carrier
$$
T=(A,B,E,F,Q,D,I,Z,H,C,P,N),
$$
the local $\NameCert_{\RolleTheoremUp}$ surface consists exactly of the finite obligation rows for endpoint real-name admission, endpoint-equality routing, continuous-map admission, regular rational readback, dyadic tolerance budgeting, intermediate-value handoff, derivative quotient inspection, terminal zero sealing, componentwise transport, displayed replay, provenance, and local naming. No obligation row may bypass the displayed $\RealUp$, $\ContinuousMapUp$, $\DerivativeUp$, $\IntermediateValueUp$, $\RegSeqRatUp$, or $\DyadicRatCoreUp$ sources.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:rolle-theorem-carrier}. The rows $A,B,E$ supply the endpoint names and the equality route, while $F$ supplies the sole continuous-map surface.

The arithmetic and localization rows are then fixed. The readback row $Q$ and the tolerance ledger $D$ are the only regular-rational and dyadic routes available to the packet, and $I$ is the only intermediate-value handoff row.

Finally inspect the derivative-facing row $Z$. It is attached to the displayed derivative quotient and terminal zero seal, and it is transported and replayed only through $H$ and $C$.

The provenance and local naming rows $P,N$ add source and name data without adding mathematical coordinates. Since the carrier has no further field, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Rolle theorem derivative-zero handoff]
\label{thm:rolle-theorem-derivative-zero-handoff}
Every derivative-zero statement exported by an accepted $\RolleTheoremUp$ carrier factors through the ordered route
$$
\RealUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \ContinuousMapUp,\ \IntermediateValueUp,\ \DerivativeUp.
$$
The exported conclusion is a displayed zero-handoff for the derivative quotient row $Z$, not a host differentiability claim and not a mean-value theorem over an ambient real function.
\end{theorem}
\begin{proof}
Start with an accepted carrier $T=(A,B,E,F,Q,D,I,Z,H,C,P,N)$. The endpoint real-name rows and the regular rational readback row are inspected before any derivative-zero read is available.

The dyadic ledger $D$ bounds the finite readback windows, and the continuous-map row $F$ fixes the displayed function data consumed by the theorem route. The intermediate-value handoff $I$ supplies the finite bisection-facing location route used by the stationary witness.

Only after these rows are present can the derivative row $Z$ be read. Transport through $H$ and replay through $C$ preserve the same order, while $P$ and $N$ add provenance and naming only.

Thus the derivative-zero export is the displayed handoff through $Z$ over the named rows. The packet contains no host differentiability predicate, no ambient mean-value theorem, and no detached equality of completed functions.
\end{proof}

\begin{theorem}[Rolle theorem Real seal non-escape]
\label{thm:rolle-theorem-real-seal-nonescape}
Every $\RealUp$ seal consumed or exported by an accepted $\RolleTheoremUp$ carrier is routed through one of the displayed endpoint, readback, intermediate-value, or derivative-zero rows of \autoref{def:rolle-theorem-carrier}. Consequently the carrier cannot export ambient $\RealUp$ completeness, trichotomy, selected roots, host differentiability, quotient real equality, or standard-bridge data.
\end{theorem}
\begin{proof}
Inspect the real-facing coordinates of the carrier. The endpoint rows $A,B$ expose the initial real names, $Q$ exposes regular rational readback, $I$ exposes the intermediate-value handoff, and $Z$ exposes the derivative-zero seal.

Each of these rows is paired with componentwise transport and displayed replay. The dyadic ledger $D$ fixes the finite tolerance budget, and the continuous-map row $F$ fixes the function surface that the route may inspect.

There is no additional coordinate for a completed-real selector, an order trichotomy witness, a selected root, a host differentiability predicate, or a bridge object. Provenance and local naming record the same row inventory.

Therefore every real seal remains inside the displayed packet boundary, and no Real or bridge claim can escape the carrier.
\end{proof}

\falsifiablePrediction{Every $\RolleTheoremUp$ read factors through endpoint $\RealUp$ names, endpoint equality, $\ContinuousMapUp$ map data, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ tolerances, $\IntermediateValueUp$ handoff, $\DerivativeUp$ zero routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{real, continuousmap, derivative, intermediatevalue, regseqrat, dyadicratcore: $\RolleTheoremUp$ is not bijective to any listed sibling because it binds endpoint equality, theorem-facing continuity, rational readback, dyadic tolerance, intermediate-value handoff, derivative-zero routing, transport, replay, provenance, and local naming as one finite carrier.}

\closureat{RolleTheoremUp}{seedStr}

\begin{closurestatus}{\RolleTheoremUp}
  \constructivestory{A $\RolleTheoremUp$ packet is generated from endpoint real-name rows, endpoint equality, continuous-map data, regular rational readback, dyadic tolerance arithmetic, intermediate-value handoff, derivative-zero routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rolle-theorem-carrier}, \autoref{thm:rolle-theorem-namecert-obligations}, \autoref{thm:rolle-theorem-derivative-zero-handoff}, and \autoref{thm:rolle-theorem-real-seal-nonescape} seed the finite theorem-facing Rolle boundary over displayed Real, continuous-map, derivative, intermediate-value, regular-rational, and dyadic rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient RealUp completeness, trichotomy, selected roots, host differentiability, quotient real equality, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, NameCert obligation coverage, derivative-zero handoff, Real seal non-escape, and TasteGate field faithfulness for BEDC.Derived.RolleTheoremUp.}
\end{closurestatus}
