\chapter{A Concrete Naming Certificate for $\RealApartnessOrderBridgeUp$}
\label{ch:concrete-instances-real-apartness-order-bridge-namecert}
\origin{human}

Following Bishop and Bridges, the $\RealApartnessOrderBridgeUp$ packet records the constructive route from positive real apartness evidence to order-facing comparison data. It consumes \autoref{ch:concrete-instances-apartnessreal-namecert}, \autoref{ch:concrete-instances-locatedreal-namecert}, \autoref{ch:concrete-instances-real-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-streamname-namecert}. The packet names the finite handoff by which a displayed positive radius can be read by order consumers without installing trichotomy, quotient real equality, a selected limit, or completeness for $\RealUp$.

\begin{definition}[RealApartnessOrderBridge carrier]
\label{def:real-apartness-order-bridge-carrier}
A $\RealApartnessOrderBridgeUp$ carrier is a finite $\BHist$ packet
$$
G=(X,Y,A,L,R,D,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two endpoint $\RealUp$ rows, exposing only their terminal real-name seals and the finite comparison handles needed by downstream order consumers.
\item $A$ is the $\ApartnessRealUp$ positive-radius witness row, binding the endpoint pair to an inspected radius seal and recording that the separation evidence is positive apartness data rather than an equality decision.
\item $L$ records the $\LocatedRealUp$ refinement rows for the two endpoints, including the located dyadic refinements used to align the endpoint windows with the positive-radius witness.
\item $R$ records the $\RegSeqRatUp$ source rows for the rational regular sequences underlying the displayed endpoint names and refinement windows.
\item $D$ records the $\DyadicRatCoreUp$ radius and comparison rows, including the positive radius token, dyadic lower-bound comparison, and finite order-facing comparison cell exported to consumers.
\item $S$ records the $\StreamNameUp$ finite window rows used to inspect the endpoint streams, radius stream, and comparison windows at the displayed precision.
\item $H$ records componentwise $\hsame$ transport for the endpoint rows, apartness witness, located refinements, regular-sequence sources, dyadic-radius and comparison rows, stream windows, provenance rows, and local naming rows.
\item $C$ records displayed $\Cont$ replay from endpoint names to stream windows, from stream windows to located dyadic refinements, from the positive-radius witness to the dyadic comparison cell, and from the comparison cell to the order-facing handoff row.
\item $P$ is the $\Pkg$ provenance over $\RealApartnessOrderBridgeUp$, $\ApartnessRealUp$, $\LocatedRealUp$, $\RealUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealApartnessOrderBridgeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for equality-or-apartness decisions, total order, quotient real equality, selected real limits, or ambient completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.RealApartnessOrderBridgeUp.RealApartnessOrderBridgeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RealApartnessOrderBridge NameCert obligations]
\label{thm:real-apartness-order-bridge-namecert-obligations}
For every accepted $\RealApartnessOrderBridgeUp$ carrier
$$
G=(X,Y,A,L,R,D,S,H,C,P,N),
$$
the local $\NameCert_{\RealApartnessOrderBridgeUp}$ surface consists exactly of the following five finite obligation rows:
\begin{enumerate}
\item endpoint admission for the two displayed $\RealUp$ rows $X,Y$;
\item positive apartness witness admission through the $\ApartnessRealUp$ row $A$;
\item located dyadic refinement admission through the $\LocatedRealUp$ row $L$;
\item rational and dyadic comparison source admission through the $\RegSeqRatUp$ and $\DyadicRatCoreUp$ rows $R,D$;
\item finite stream-window admission through the $\StreamNameUp$ row $S$.
\end{enumerate}
The structural rows $H,C,P,N$ transport, replay, source, and name only these five obligation rows. No order-facing handoff obligation is stored outside the displayed carrier.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-apartness-order-bridge-carrier}. The endpoint rows $X,Y$ supply the two displayed real-name surfaces, and the apartness row $A$ supplies the positive-radius witness attached to that endpoint pair.

The refinement and source rows are then fixed. The row $L$ is the only located-refinement surface, while $R$ and $D$ are the only rational and dyadic rows that expose the radius and comparison data.

Finally inspect the finite-window row $S$. It is the only stream-name surface from which the endpoint, radius, and comparison windows are read.

The remaining rows $H,C,P,N$ preserve, replay, source, and name the same data. Since the carrier has no additional coordinate, the listed five rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[RealApartnessOrderBridge positive order handoff]
\label{thm:real-apartness-order-bridge-positive-order-handoff}
Every order-facing consumer read exported by an accepted $\RealApartnessOrderBridgeUp$ carrier factors through the displayed positive-separation handoff formed by the $\ApartnessRealUp$ witness row $A$, the $\LocatedRealUp$ refinement row $L$, the $\DyadicRatCoreUp$ comparison row $D$, and the finite $\StreamNameUp$ windows $S$. The consumer may read only this finite positive-separation handoff, not an ambient comparison principle.
\end{theorem}
\begin{proof}
Start with an accepted carrier $G=(X,Y,A,L,R,D,S,H,C,P,N)$. The endpoint rows expose the two real names before any order-facing read is available.

Read the positive-radius witness $A$ together with the located refinements $L$. These rows bind the apartness evidence to displayed dyadic windows rather than to a host comparison of completed reals.

The dyadic comparison row $D$ and stream-window row $S$ then provide the finite comparison cell consumed by an order-facing reader. Transport and replay through $H$ and $C$ preserve that same row inventory, while $P$ and $N$ add only provenance and local naming.

Thus every exported consumer read factors through the displayed positive-separation handoff. The packet contains no separate ambient comparison principle or selected real object.
\end{proof}

\begin{theorem}[RealApartnessOrderBridge no trichotomy]
\label{thm:real-apartness-order-bridge-no-trichotomy}
An accepted $\RealApartnessOrderBridgeUp$ carrier exports no equality-or-apartness decision, total order on $\RealUp$, quotient real, selected limit, or $\RealUp$ completeness principle. Its public content is only the finite positive-separation handoff described by the displayed endpoint, apartness, located-refinement, rational-source, dyadic-comparison, stream-window, transport, replay, provenance, and naming rows.
\end{theorem}
\begin{proof}
Project the rows of \autoref{def:real-apartness-order-bridge-carrier}. The endpoint rows, positive-radius witness, located refinements, rational sources, dyadic comparison rows, and stream windows are the only mathematical data coordinates in the carrier.

None of these rows stores a trichotomy branch, quotient constructor, equality decision, selected limit, or completeness witness. The apartness row records positive evidence, and the comparison row records only the finite handoff cell derived from that evidence.

The structural rows $H,C,P,N$ cannot create new mathematical coordinates; they only transport, replay, source, and name the displayed rows. Therefore the packet exports the stated positive-separation handoff and none of the listed excluded principles.
\end{proof}

\falsifiablePrediction{Every $\RealApartnessOrderBridgeUp$ order-facing read factors through two endpoint $\RealUp$ rows, an $\ApartnessRealUp$ positive-radius witness, $\LocatedRealUp$ refinement rows, $\RegSeqRatUp$ source rows, $\DyadicRatCoreUp$ radius and comparison rows, $\StreamNameUp$ finite windows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{apartnessreal, locatedreal, real, regseqrat, dyadicratcore, streamname: $\RealApartnessOrderBridgeUp$ is not bijective to any listed sibling because it jointly carries endpoint names, a positive apartness witness, located refinements, rational sequence sources, dyadic radius and comparison data, finite stream windows, transport, replay, provenance, and local naming as one order-facing handoff packet.}

\closureat{RealApartnessOrderBridgeUp}{seedStr}

\begin{closurestatus}{\RealApartnessOrderBridgeUp}
  \constructivestory{A $\RealApartnessOrderBridgeUp$ packet is generated from two endpoint $\RealUp$ rows, an $\ApartnessRealUp$ positive-radius witness, $\LocatedRealUp$ refinement rows, $\RegSeqRatUp$ source rows, $\DyadicRatCoreUp$ radius and comparison rows, $\StreamNameUp$ finite windows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-apartness-order-bridge-carrier}, \autoref{thm:real-apartness-order-bridge-namecert-obligations}, \autoref{thm:real-apartness-order-bridge-positive-order-handoff}, and \autoref{thm:real-apartness-order-bridge-no-trichotomy} seed the finite positive-apartness route from endpoint real names to order-facing comparison data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close equality-or-apartness decisions, total order on RealUp, quotient real construction, selected limits, RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, positive-radius handoff, no-trichotomy boundary, and TasteGate field faithfulness for BEDC.Derived.RealApartnessOrderBridgeUp.}
\end{closurestatus}
