\chapter{A Concrete Naming Certificate for $\RaabeDuhamelTestUp$}
\label{ch:concrete-instances-raabe-duhamel-test-namecert}
\origin{human}

Following Raabe and Duhamel, and Bishop--Bridges constructive analysis, the $\RaabeDuhamelTestUp$ packet records the finite first-order ratio-defect test that turns displayed tail estimates into a regular rational convergence route before any Real-facing consumer reads a seal. It sits beside the ratio-test route of \autoref{ch:concrete-instances-regular-cauchy-ratio-test-namecert}, the comparison-test route of \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a finite convergence-test boundary for the Phase Real and Completion route; it is not host summability, quotient series equality, selected sums, countable choice, trichotomy, or $\RealUp$ completeness.

\begin{definition}[Raabe--Duhamel test carrier]\label{def:raabe-duhamel-test-carrier}
A $\RaabeDuhamelTestUp$ carrier is a finite $\BHist$ packet
$$
R=(A,Q,M,D,W,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the source series row, exposing only the inspected term windows and partial-sum windows used by the current tail request.
\item $Q$ is the positive-tail quotient row, recording the finite adjacent-term quotient windows on which the Raabe--Duhamel defect is read.
\item $M$ is the displayed defect-modulus row, assigning each requested tail budget a finite threshold and a rational margin witnessing that the inspected quotient defect stays beyond the chosen comparison boundary.
\item $D$ is the dyadic domination ledger, converting the defect and threshold rows into a finite majorant comparison usable by the regular Cauchy comparison-test surface.
\item $W$ is the $\StreamNameUp$ finite-window row for the displayed partial sums and comparison majorants.
\item $T$ is the $\RegularCauchyComparisonTestUp$ handoff row that consumes $D$ and $W$ before any regular Cauchy conclusion is exposed.
\item $E$ is the endpoint route through $\RegSeqRatUp$ and the terminal $\RealUp$ seal reached only after $T$ has been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source, quotient, defect-modulus, domination, window, comparison, endpoint, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from each tail request through $M,D,W,T,E$.
\item $P$ is the $\Pkg$ provenance over $\RaabeDuhamelTestUp$, $\RegularCauchyRatioTestUp$, $\RegularCauchyComparisonTestUp$, $\RegSeqRatUp$, $\RealUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RaabeDuhamelTestUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,Q,M,D,W,T,E,H,C,P,N$. It has no coordinate for host summability, quotient series equality, selected sums, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Raabe--Duhamel test NameCert obligations]\label{thm:raabe-duhamel-test-namecert-obligations}
For every accepted $\RaabeDuhamelTestUp$ carrier
$$
R=(A,Q,M,D,W,T,E,H,C,P,N),
$$
the local $\NameCert_{\RaabeDuhamelTestUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source series row, adjacent-term quotient row, defect-modulus row, dyadic domination ledger, finite window row, comparison-test handoff, endpoint route, transport, replay, provenance, and local naming row;
\item quotient-window exactness, requiring every accepted defect read to pass through the displayed source and adjacent-term quotient windows $A,Q$;
\item defect-modulus stability, requiring the threshold and rational margin in $M$ to be the only data used to choose the tail budget;
\item domination routing, requiring $D$ and $W$ to convert the displayed defect data into the same finite comparison windows consumed by $T$;
\item regular and Real handoff, requiring every endpoint-facing read to pass through $T$ and then $E$ before a $\RegSeqRatUp$ or $\RealUp$ consumer receives data;
\item ledger non-escape, requiring $H,C,P,N$ to transport, replay, source, and name only the displayed rows and to exclude host summability, quotient series equality, selected sums, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:raabe-duhamel-test-carrier}. Carrier admission is exactly the inventory $A,Q,M,D,W,T,E,H,C,P,N$, so the local certificate has no detached row for an infinite sum, quotient series equality, or ambient completeness.

The quotient-window and defect-modulus clauses are read before the comparison handoff. The source row $A$ exposes the inspected terms and partial sums, the row $Q$ exposes only adjacent-term quotient windows, and $M$ records the finite threshold and rational margin used by the current tail request.

The domination route is then forced through $D,W,T$. The dyadic ledger $D$ converts the displayed defect data into a majorant comparison, the window row $W$ fixes the finite stream windows, and the comparison-test row $T$ is the only route that may export a regular Cauchy conclusion.

Finally, $E$ supplies the regular rational and Real-facing handoff. The remaining rows $H,C,P,N$ preserve, replay, source, and name the same route, so none of them can introduce host summability, quotient series equality, selected sums, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge data.
\end{proof}

\begin{theorem}[Raabe--Duhamel test tail handoff]\label{thm:raabe-duhamel-test-tail-handoff}
Every accepted $\RaabeDuhamelTestUp$ read reaching a $\RegSeqRatUp$ or $\RealUp$ consumer factors through the finite route
$$
A,Q\longmapsto M\longmapsto D,W\longmapsto T\longmapsto E\longmapsto (H,C,P,N).
$$
Thus a Phase Real or Completion consumer receives tail convergence data only after the source series row, adjacent-term quotient row, defect threshold, dyadic domination ledger, finite windows, comparison-test handoff, endpoint route, transport, replay, provenance, and local NameCert have all been displayed.
\end{theorem}
\begin{proof}
Begin with an endpoint-facing read of an accepted carrier. By \autoref{def:raabe-duhamel-test-carrier}, the only term-level data available before the defect estimate are $A$ and $Q$, so the read first consumes the displayed source windows and adjacent-term quotient windows.

The tail budget is then forced through $M$. This row names the finite threshold and rational margin attached to the requested tail, and it contributes no selected infinite sum or host summability theorem.

Next the comparison route passes through $D,W,T$. The dyadic domination ledger $D$ and finite window row $W$ prepare exactly the rows consumed by $\RegularCauchyComparisonTestUp$ in $T$, matching the sibling route named by \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}.

Only after that comparison row has been displayed can the packet reach $E$, the regular rational and Real-facing endpoint route. The structural rows $H,C,P,N$ preserve this same route by transport, replay, provenance, and local naming, so no consumer can bypass it through quotient series equality, selected sums, countable choice, trichotomy, host summability, or ambient $\RealUp$ completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\RaabeDuhamelTestUp$ endpoint-facing read factors through source series windows, adjacent-term quotient windows, a defect-modulus row, dyadic domination, StreamName windows, a RegularCauchyComparisonTest handoff, RegSeqRat and RealUp endpoint routing, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{regularcauchyratiotest, regularcauchycomparisontest, regseqrat, real: $\RaabeDuhamelTestUp$ is not bijective to any listed sibling because it jointly carries adjacent-term quotient windows, a defect-modulus threshold, dyadic domination, comparison-test handoff, regular rational endpoint routing, Real sealing, transport, replay, provenance, and local naming.}

\closureat{RaabeDuhamelTestUp}{seedStr}

\begin{closurestatus}{\RaabeDuhamelTestUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:raabe-duhamel-test-carrier}, \autoref{thm:raabe-duhamel-test-namecert-obligations}, and \autoref{thm:raabe-duhamel-test-tail-handoff} seed the finite Raabe--Duhamel convergence-test boundary over displayed quotient-defect, domination, comparison, $\RegSeqRatUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host summability, quotient series equality, selected sums, countable choice, trichotomy, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean theorems for carrier admission, quotient-window exactness, defect-modulus stability, domination routing, regular and Real handoff, ledger non-escape, and TasteGate field faithfulness for BEDC.Derived.RaabeDuhamelTestUp.}
  \constructivestory{A $\RaabeDuhamelTestUp$ packet is generated from source series windows, adjacent-term quotient windows, a displayed defect modulus, dyadic domination, StreamName windows, a RegularCauchyComparisonTest handoff, RegSeqRat and RealUp endpoint routing, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
