\chapter{A Concrete Naming Certificate for $\BolzanoCauchyUp$}
\label{ch:concrete-instances-bolzano-cauchy-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\BolzanoCauchyUp$ packet records the constructive bidirectional Cauchy convergence criterion as finite BEDC NameCert data. It sits over the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the $\RealUp$ seal surface of \autoref{ch:concrete-instances-real-namecert}, the explicit criterion route of \autoref{ch:concrete-instances-cauchy-convergence-criterion-namecert}, and the limit-seal boundary of \autoref{ch:concrete-instances-cauchylimitseal-namecert}. The packet names the two constructive directions as displayed rows; it is not ambient $\RealUp$ completeness, quotient stream equality, a selected host limit, trichotomy, open-cover compactness, countable choice, or bridge checking.

\begin{definition}[Bolzano-Cauchy carrier]
\label{def:bolzano-cauchy-carrier}
A $\BolzanoCauchyUp$ carrier is a finite $\BHist$ packet
$$
B=(S,M,D,R,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ window schedule exposing exactly the finite observations of the candidate sequence.
\item $M$ is the Cauchy modulus data assigning each dyadic tolerance request a displayed threshold for the windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the dyadic scales, rational comparisons, and exhaustion budget used by both directions.
\item $R$ is the $\RegSeqRatUp$ readback row produced from $S,M,D$.
\item $E$ is the $\RealUp$ seal row obtained after the criterion route has displayed the regular rational handoff.
\item $L$ is the $\CauchyLimitSealUp$ compatibility row that binds the same $S,M,D,R,E$ route to a limit-seal consumer.
\item $H$ records componentwise $\hsame$ transport for the stream schedule, modulus data, dyadic ledger, regular readback, Real seal, limit-seal compatibility, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tolerance request through $S,M,D,R,E,L$ and then through the structural rows.
\item $P$ is the $\Pkg$ provenance over $\BolzanoCauchyUp$, $\CauchyConvergenceCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CauchyLimitSealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BolzanoCauchyUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It contains no coordinate for ambient $\RealUp$ completeness, quotient stream equality, a selected host limit, trichotomy, open-cover compactness, countable choice, or a detached limit seal.
\end{definition}

\begin{theorem}[Bolzano-Cauchy NameCert obligations]
\label{thm:bolzano-cauchy-namecert-obligations}
For every accepted $\BolzanoCauchyUp$ carrier
$$
B=(S,M,D,R,E,L,H,C,P,N),
$$
the local $\NameCert_{\BolzanoCauchyUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed stream schedule, Cauchy modulus data, dyadic tolerance ledger, regular readback, Real seal, limit-seal compatibility, transport, continuation, provenance, and local name;
\item Cauchy-to-limit routing, requiring any Cauchy-read consumer to pass through $S,M,D,R$ before $E$ or $L$ is available;
\item limit-to-Cauchy routing, requiring any limit-seal read to replay the same $S,M,D,R$ tolerance route before it can export a Cauchy conclusion;
\item ledger exactness, requiring every tolerance request in either direction to be accounted for by $D$ and sourced by $P$;
\item structural stability, requiring $H$ and $C$ to preserve and replay only the displayed rows.
\end{enumerate}
No Bolzano-Cauchy obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bolzano-cauchy-carrier}. The visible coordinates are exactly the stream schedule, modulus data, dyadic ledger, regular readback, Real seal, limit-seal compatibility, transport, continuation, provenance, and local naming rows.

The two route obligations are forced by the displayed order. A Cauchy-read consumer has no source except the windows $S$, thresholds $M$, ledger $D$, and readback $R$ before the Real and limit-seal rows are exposed. Conversely, a limit-seal consumer reading $L$ must replay the same finite tolerance route before it can return a Cauchy conclusion.

The ledger and structural rows then exhaust the remaining obligations. The dyadic row $D$ accounts for every tolerance request, the provenance row $P$ records its source, and $H,C$ can only transport and replay the displayed packet. Since the carrier has no additional coordinate, the five listed rows are the complete local NameCert surface.
\end{proof}

\begin{theorem}[Bolzano-Cauchy Cauchy-to-limit route]
\label{thm:bolzano-cauchy-cauchy-to-limit-route}
Every $\RealUp$-facing read of an accepted $\BolzanoCauchyUp$ carrier that begins from the Cauchy side factors through the finite route
$$
S \longmapsto M \longmapsto D \longmapsto R \longmapsto E \longmapsto L
$$
and then through the stored $\hsame$ transport $H$, $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. The route is the $\CauchyConvergenceCriterionUp$ handoff read through a $\CauchyLimitSealUp$ compatibility boundary; it exports no ambient completeness theorem, quotient stream, selected host limit, trichotomy row, open-cover compactness row, countable choice principle, or detached seal.
\end{theorem}
\begin{proof}
Start with an accepted Cauchy-side read. By carrier admission, the only sequence data are the finite windows $S$, and the only tolerance data are the threshold row $M$ and dyadic ledger $D$.

Apply the existing convergence-criterion route from \autoref{ch:concrete-instances-cauchy-convergence-criterion-namecert}. Its readback stage is the displayed $\RegSeqRatUp$ row $R$, and its Real-facing endpoint is the seal row $E$.

The Bolzano-Cauchy packet adds no new endpoint between $E$ and the limit-seal consumer. The compatibility row $L$ reads the same finite handoff, while $H,C,P,N$ transport, replay, source, and name that packet.

Thus the Cauchy-side read reaches the limit-seal boundary only through the displayed route. The carrier inventory excludes ambient completeness, quotient streams, selected host limits, trichotomy, open-cover compactness, countable choice, and detached seals.
\end{proof}

\begin{theorem}[Bolzano-Cauchy limit-to-Cauchy route]
\label{thm:bolzano-cauchy-limit-to-cauchy-route}
Every limit-facing read of an accepted $\BolzanoCauchyUp$ carrier that begins from the $\CauchyLimitSealUp$ row factors back through the same displayed route
$$
L \longmapsto E \longmapsto R \longmapsto D \longmapsto M \longmapsto S
$$
as a Cauchy conclusion over the finite stream windows. The reverse direction uses only the stored compatibility, Real seal, regular readback, dyadic ledger, modulus data, stream schedule, transport, continuation, provenance, and local NameCert rows; it does not use ambient $\RealUp$ completeness, quotient stream equality, a selected host limit, trichotomy, open-cover compactness, countable choice, or bridge checking.
\end{theorem}
\begin{proof}
Begin with a limit-facing read of the row $L$. By \autoref{def:bolzano-cauchy-carrier}, that row is compatible only with the displayed $S,M,D,R,E$ route and has no independent source of sequence or limit data.

Read the Real and regular-rational stages next. The row $E$ is downstream of $R$, and $R$ is downstream of the same dyadic ledger and modulus data used by the Cauchy side. Hence the reverse read cannot bypass $D$ or $M$.

Finally return to the finite stream windows. The schedule $S$ is the only observation source, and $H,C,P,N$ merely preserve, replay, source, and name the same packet. Therefore the limit-facing read yields a Cauchy conclusion only over the displayed finite windows, with no appeal to ambient completeness, quotient streams, selected host limits, trichotomy, open-cover compactness, countable choice, or bridge checking.
\end{proof}

\begin{theorem}[Bolzano-Cauchy subsequence window extraction]
\label{thm:bolzano-cauchy-subsequence-window-extraction}
An accepted $\BolzanoCauchyUp$ packet with a bounded finite $\RealUp$ sequence window exposes a finite subsequence-window route before any Cauchy read or limit read is exported. The extracted route is carried by the displayed $\StreamNameUp$ window schedule $S$, dyadic tolerance ledger $D$, $\RegSeqRatUp$ readback row $R$, and terminal $\RealUp$ seal row $E$, together with the same $M,L,H,C,P,N$ support rows of the packet.

This extraction exports no selected host limit, countable-choice subsequence selector, ambient completeness principle, open-cover compactness row, quotient stream equality, or detached limit seal.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bolzano-cauchy-carrier}. The bounded finite sequence window can only be read through the displayed StreamName schedule $S$, the modulus data $M$, the dyadic ledger $D$, and the regular readback row $R$.

Apply the NameCert obligations of \autoref{thm:bolzano-cauchy-namecert-obligations}. They force any Cauchy-side or limit-side consumer to use the displayed window, modulus, ledger, readback, seal, and compatibility rows before the local certificate can be consumed.

Use \autoref{thm:bolzano-cauchy-cauchy-to-limit-route} and \autoref{thm:bolzano-cauchy-limit-to-cauchy-route}. Both directions pass through the same $S,M,D,R,E,L$ surface, so a finite subsequence-window read is exposed at the StreamName and RegSeqRat stages before either route exports a Cauchy or limit conclusion.

The structural rows $H,C,P,N$ only transport, replay, source, and name that finite packet. Because the carrier has no coordinate for selected host limits, countable-choice selectors, ambient completeness, open-cover compactness, quotient stream equality, or detached limit seals, the extraction remains a finite subsequence-window route.
\end{proof}

\closureat{BolzanoCauchyUp}{seedStr}

\begin{closurestatus}{\BolzanoCauchyUp}
  \constructivestory{A $\BolzanoCauchyUp$ packet is generated from a finite StreamName window schedule, Cauchy modulus data, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, CauchyLimitSeal compatibility row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bolzano-cauchy-carrier}, \autoref{thm:bolzano-cauchy-namecert-obligations}, \autoref{thm:bolzano-cauchy-cauchy-to-limit-route}, and \autoref{thm:bolzano-cauchy-limit-to-cauchy-route} seed the finite bidirectional Cauchy convergence criterion over StreamName windows, Cauchy modulus data, DyadicRatCore tolerance rows, RegSeqRat readback, RealUp seal, and CauchyLimitSeal compatibility.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient RealUp completeness, quotient stream equality, selected host limits, trichotomy, open-cover compactness, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Cauchy-to-limit routing, limit-to-Cauchy routing, ledger exactness, and structural stability for BEDC.Derived.BolzanoCauchyUp.}
\end{closurestatus}
