\chapter{A Concrete Naming Certificate for $\RegularCauchySubsequenceInvarianceUp$}
\label{ch:concrete-instances-regular-cauchy-subsequence-invariance-namecert}
\origin{human}

Following Bishop and Bridges' constructive Cauchy sequence discipline, the $\RegularCauchySubsequenceInvarianceUp$ packet records the finite BEDC route by which a cofinal subsequence of a regular Cauchy row preserves the same Real-facing seal. It consumes the subsequence interface of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert}, the cofinal selector surface of \autoref{ch:concrete-instances-cofinalsubsequence-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet names invariance as displayed finite routing data, not as quotient stream equality, selected limit choice, host real equality, or ambient Real completeness.

\begin{definition}[Regular-Cauchy subsequence invariance carrier]
\label{def:regular-cauchy-subsequence-invariance-carrier}
A $\RegularCauchySubsequenceInvarianceUp$ carrier is a finite $\BHist$ packet
$$
I=(Q,F,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the source regular Cauchy row whose Real-facing seal is being preserved.
\item $F$ is the $\CofinalSubsequenceUp$ selector row, carrying only displayed monotone and cofinal access to source indices.
\item $S$ is the $\StreamNameUp$ window ledger for the source and selected subsequence windows inspected along $F$.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from the selected windows and the regular Cauchy source.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger shared by the source row, selected windows, readback row, and Real-facing seal.
\item $E$ is the $\RealUp$ seal exposed after $Q,F,S,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source row, cofinal selector, stream windows, readback row, dyadic ledger, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any finite subsequence read back through $F,S,R,D$ before the seal row $E$ is reached.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchySubsequenceInvarianceUp$, $\RegularCauchySubsequenceUp$, $\CofinalSubsequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchySubsequenceInvarianceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,F,S,R,D,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular-Cauchy subsequence invariance NameCert obligations]
\label{thm:regular-cauchy-subsequence-invariance-namecert-obligations}
For every accepted $\RegularCauchySubsequenceInvarianceUp$ carrier
$$
I=(Q,F,S,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchySubsequenceInvarianceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source regular Cauchy row, cofinal selector, stream-window ledger, regular rational readback, dyadic tolerance ledger, Real seal, componentwise transport, continuation replay, provenance, and local naming rows;
\item cofinal access, requiring every selected index read to pass through the displayed selector row $F$ rather than through an external choice function;
\item window alignment, requiring every subsequence observation to be one of the finite $\StreamNameUp$ windows named by $S$;
\item readback exactness, requiring $R$ to read only the selected windows from $S$ and the source regular Cauchy row $Q$;
\item tolerance preservation, requiring the dyadic ledger $D$ to be the same ledger consumed by $Q$, $S$, $R$, and the seal row $E$;
\item Real-seal non-escape, requiring $E$ to be reached only after $F,S,R,D$ have displayed the subsequence route from $Q$.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-subsequence-invariance-carrier}. The visible analytic rows are exactly the source row $Q$, the cofinal selector $F$, stream windows $S$, regular rational readback $R$, dyadic ledger $D$, and Real seal $E$.

Cofinal access is read from $F$. Since every selected index must enter through that row, the certificate never calls on a detached infinite choice function or host subsequence object.

Window alignment and readback exactness are read from $S$ and $R$. The selected observations are the finite windows named by $S$, and $R$ can only replay those windows against the source row $Q$.

Tolerance preservation is the projection to $D$. The source row, selected windows, readback row, and Real seal all consume that same dyadic ledger, so no second tolerance budget can alter the subsequence read.

Finally, $H,C,P,N$ transport, replay, source, and name only the displayed packet rows. The excluded quotient, choice, selected-limit, host-equality, completeness, Lean, and bridge data therefore have no coordinate in the local NameCert surface.
\end{proof}

\begin{theorem}[Regular-Cauchy subsequence invariance cofinal route]
\label{thm:regular-cauchy-subsequence-invariance-cofinal-route}
Let $I=(Q,F,S,R,D,E,H,C,P,N)$ be an accepted $\RegularCauchySubsequenceInvarianceUp$ carrier. Every subsequence read from $I$ factors through the cofinal route
$$
Q,F,S,R,D,E.
$$
In particular, the read reaches the Real-facing seal only after the source regular Cauchy row, cofinal selector, finite stream windows, regular rational readback, and dyadic tolerance ledger have all been displayed.
\end{theorem}
\begin{proof}
Begin with a subsequence read of the accepted packet. The only selector coordinate is $F$, so the read first factors from the source row $Q$ through the displayed cofinal access row.

The selected observation is then forced into the finite window ledger $S$. Since the carrier has no host stream coordinate, each inspected value is read through one of the displayed $\StreamNameUp$ windows.

The regular rational readback and tolerance rows come next. The row $R$ replays the selected windows as regular rational data, and $D$ supplies the shared dyadic tolerance ledger used by both the source row and the selected readback.

The Real-facing seal is downstream of those rows. Thus the read reaches $E$ only through $Q,F,S,R,D$, and the support rows $H,C,P,N$ cannot add another analytic route.
\end{proof}

\begin{theorem}[Regular-Cauchy subsequence invariance Real seal non-escape]
\label{thm:regular-cauchy-subsequence-invariance-real-seal-nonescape}
For every accepted $\RegularCauchySubsequenceInvarianceUp$ carrier
$$
I=(Q,F,S,R,D,E,H,C,P,N),
$$
the public export is the displayed finite route from the source regular Cauchy row to the Real-facing seal. It exports no quotient stream equality, selected limit, countable choice principle, host real equality, ambient Real completeness, independent Real carrier, Lean credential, or bridge credential.
\end{theorem}
\begin{proof}
Use \autoref{thm:regular-cauchy-subsequence-invariance-cofinal-route}. Every Real-facing subsequence read has already passed through the source row, cofinal selector, finite stream windows, regular rational readback, and dyadic tolerance ledger before it reaches $E$.

The carrier has no remaining analytic coordinate. The transport, replay, provenance, and naming rows preserve the displayed route, but they do not introduce quotient representatives, selected limits, choice principles, host equality witnesses, completeness principles, or independent Real carriers.

Therefore the public export is exactly the finite seal-preserving route described above. The omitted Lean and bridge credentials are also not exported, because this seed packet records only the paper-side finite NameCert surface.
\end{proof}

\closureat{RegularCauchySubsequenceInvarianceUp}{seedStr}

\begin{closurestatus}{\RegularCauchySubsequenceInvarianceUp}
  \constructivestory{A $\RegularCauchySubsequenceInvarianceUp$ packet is generated from a source regular Cauchy row, a cofinal selector row, finite StreamName windows, RegSeqRat readback, a shared DyadicRatCore tolerance ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-subsequence-invariance-carrier}, \autoref{thm:regular-cauchy-subsequence-invariance-namecert-obligations}, \autoref{thm:regular-cauchy-subsequence-invariance-cofinal-route}, and \autoref{thm:regular-cauchy-subsequence-invariance-real-seal-nonescape} seed the finite cofinal-subsequence route preserving the same Real-facing regular Cauchy seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim full Real completeness, selected limits, quotient stream equality, countable choice, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Formal closure requires checked carrier admission, cofinal-route factorization, tolerance preservation, and Real-seal non-escape theorems under BEDC.Derived.RegularCauchySubsequenceInvarianceUp.}
\end{closurestatus}
