\chapter{A Concrete Naming Certificate for $\RegularCauchyModulusRealizerUp$}
\label{ch:concrete-instances-regular-cauchy-modulus-realizer-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\RegularCauchyModulusRealizerUp$ packet records the finite request-to-tail-window realizer by which a regular Cauchy modulus becomes a displayed regular rational read before the terminal $\RealUp$ seal is consumed. It sits over the source decoding of \autoref{ch:concrete-instances-cauchy-realizer-namecert}, the Real-facing threshold route of \autoref{ch:concrete-instances-realcauchymodulus-namecert}, the generic Cauchy-modulus schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies the L10 Real and Completion route with one finite witness object for turning a precision request into the tail window it reads; it is not Real completeness, quotient stream equality, host real equality, countable choice, a selected limit, trichotomy, or a standard bridge.

\begin{definition}[Regular Cauchy modulus realizer carrier]
\label{def:regular-cauchy-modulus-realizer-carrier}
A $\RegularCauchyModulusRealizerUp$ carrier is a finite $\BHist$ packet
$$
R=(A,M,W,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the precision request row, recording the finite Real or Completion demand that must be answered by a tail-window read.
\item $M$ is the Cauchy-modulus threshold row imported from the Real-facing modulus route and the generic modulus schedule.
\item $W$ is the selected finite $\StreamNameUp$ tail-window row determined by $A$ and $M$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, storing the requested radius, slack comparisons, and dyadic arithmetic consumed by the selected window.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the window $W$ under the tolerance ledger $D$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the request, threshold, window, tolerance, and readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the request, modulus threshold, selected window, tolerance ledger, readback, seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from the precision request through $A,M,W,D,Q,E$ and then through $H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyModulusRealizerUp$, $\CauchyRealizerUp$, $\RealCauchyModulusUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyModulusRealizerUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $A,M,W,D,Q,E,H,C,P,N$. It has no coordinate for Real completeness, quotient stream equality, host real equality, countable choice, a selected limit, trichotomy, open-cover compactness, Lean verification, or a standard bridge.
\end{definition}

\begin{theorem}[Regular Cauchy modulus realizer NameCert obligations]
\label{thm:regular-cauchy-modulus-realizer-namecert-obligations}
For every accepted $\RegularCauchyModulusRealizerUp$ carrier
$$
R=(A,M,W,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyModulusRealizerUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the precision request $A$, Cauchy-modulus threshold $M$, selected tail window $W$, dyadic tolerance ledger $D$, regular rational readback $Q$, terminal $\RealUp$ seal $E$, and structural rows $H,C,P,N$;
\item request admission, requiring the Real or Completion precision request to enter through $A$ before any threshold or window is read;
\item threshold realization, requiring the threshold row $M$ to be the only Cauchy-modulus source used to select the tail window;
\item tail-window selection, requiring $W$ to be the finite $\StreamNameUp$ row selected by the pair $A,M$;
\item tolerance accounting, requiring $D$ to record exactly the dyadic radius and slack comparisons consumed by $W,Q,E$;
\item readback and seal routing, requiring $Q$ and $E$ to be downstream of the displayed $A,M,W,D$ route;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$;
\item non-escape for Real completeness, quotient stream equality, host real equality, countable choice, selected limits, trichotomy, open-cover compactness, Lean verification, and standard-bridge data.
\end{enumerate}
No regular Cauchy modulus realizer obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-modulus-realizer-carrier}. The precision request $A$, threshold row $M$, tail window $W$, tolerance ledger $D$, regular readback $Q$, and terminal seal $E$ are the only analytic coordinates, while $H,C,P,N$ are the only structural coordinates.

The request-to-window order is forced by the displayed tuple. A consumer first reads $A$, then the threshold row $M$, and only then the finite $\StreamNameUp$ window $W$ selected for the requested tolerance.

The tolerance and seal rows are downstream. The ledger $D$ supplies the dyadic radius and slack comparisons used by the regular readback $Q$, and the seal $E$ is reached after those rows have been displayed.

The structural rows transport, replay, source, and name the same route. Since none of the excluded objects appears as a carrier coordinate, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Regular Cauchy modulus realizer tail realization]
\label{thm:regular-cauchy-modulus-realizer-tail-realization}
Every Real or Completion precision request accepted by a $\RegularCauchyModulusRealizerUp$ carrier factors through the finite route
$$
A\longmapsto M\longmapsto W\longmapsto D\longmapsto Q\longmapsto E\longmapsto H,C,P,N .
$$
Consequently the consumer receives a displayed request row, a Cauchy-modulus threshold, one selected finite $\StreamNameUp$ tail window, a $\DyadicRatCoreUp$ tolerance ledger, a $\RegSeqRatUp$ readback, a terminal $\RealUp$ seal, componentwise transport, continuation replay, provenance, and local naming. The factorization supplies no ambient completeness principle, quotient stream equality, host equality, countable-choice selector, selected limit, trichotomy row, open-cover compactness theorem, Lean evidence, or standard bridge.
\end{theorem}
\begin{proof}
Start with an accepted carrier and inspect its precision request row. The row $A$ is the only entrance for the requested tolerance, so a consumer cannot first read a detached stream window or terminal Real seal.

The threshold row is read next. The row $M$ is the only Cauchy-modulus coordinate in the carrier, hence it is the only source from which the tail boundary for the request can be obtained.

Once $A$ and $M$ are fixed, the selected window $W$ is the finite stream row consumed by the readback. The dyadic ledger $D$ then records the tolerance arithmetic for that window, and $Q$ is the regular rational observation obtained from the same displayed data.

Finally the seal $E$ and structural rows $H,C,P,N$ close the finite route. They preserve and name the displayed path, but they introduce none of the excluded completeness, quotient, choice, order, verification, or bridge data.
\end{proof}

\begin{theorem}[Regular Cauchy modulus realizer request transport determinacy]
\label{thm:regular-cauchy-modulus-realizer-request-transport-determinacy}
Let
$$
R=(A,M,W,D,Q,E,H,C,P,N)
$$
and
$$
R'=(A',M',W',D',Q',E',H',C',P',N')
$$
be accepted $\RegularCauchyModulusRealizerUp$ carriers. Suppose the precision request rows $A,A'$ and Cauchy-modulus threshold rows $M,M'$ are carried to one another by the displayed componentwise $\hsame$ rows in $H,H'$, and suppose the displayed $\Cont$ replays in $C,C'$ read the same request-to-threshold route. Then the selected $\StreamNameUp$ tail-window rows $W,W'$, the $\DyadicRatCoreUp$ tolerance ledgers $D,D'$, the $\RegSeqRatUp$ readbacks $Q,Q'$, and the terminal $\RealUp$ seal rows $E,E'$ are the same classifier-facing finite route. The determinacy result exports no selected limit, quotient stream equality, host real equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or standard bridge.
\end{theorem}
\begin{proof}
Project the two carrier presentations of \autoref{def:regular-cauchy-modulus-realizer-carrier}. In each accepted packet the only entrance for a precision demand is the request row, and the only threshold source downstream of it is the Cauchy-modulus row.

Use the ordering supplied by \autoref{thm:regular-cauchy-modulus-realizer-tail-realization}. Both displayed replays read the route from $A$ to $M$ and from $A'$ to $M'$ before any window, ledger, readback, or seal row is exposed. The hypotheses identify the request and threshold rows through the componentwise $\hsame$ data in $H,H'$.

After that identification, the accepted carrier has a single downstream window coordinate for the fixed request-threshold pair: $W$ in $R$ and $W'$ in $R'$. The dyadic tolerance ledger is then the single row downstream of the selected window, so the classifier-facing ledger route is $D,D'$.

The readback and seal rows are forced in the same way. The only $\RegSeqRatUp$ readback downstream of the ledger is $Q,Q'$, and the only terminal $\RealUp$ seal downstream of that readback is $E,E'$.

Finally apply the non-escape boundary of \autoref{thm:regular-cauchy-modulus-realizer-nonescape}. Since neither carrier contains any coordinate for selected limits, quotient stream equality, host real equality, countable choice, trichotomy, ambient completeness, Lean evidence, or a standard bridge, the transported request can select only the finite route through $W,D,Q,E$ and its counterpart $W',D',Q',E'$.
\end{proof}

\begin{theorem}[Regular Cauchy modulus realizer selector budget exhaustion]
\label{thm:regular-cauchy-modulus-realizer-selector-budget-exhaustion}
Let
$$
R=(A,M,W,D,Q,E,H,C,P,N)
$$
be an accepted $\RegularCauchyModulusRealizerUp$ carrier. Any $\RealObservationBudgetUp$ consumer or $\FiniteObservationBudgetSelectorUp$ consumer serving the same precision request factors through
$$
A\longmapsto M\longmapsto W\longmapsto D\longmapsto Q\longmapsto E
$$
and then through the structural rows $H,C,P,N$ of $R$. The selector receives no independent stream representative, hidden schedule, selected limit, quotient equality, countable-choice row, trichotomy row, or ambient $\RealUp$ completeness datum. Thus the budget consumers of \autoref{ch:concrete-instances-real-observation-budget-namecert} and \autoref{ch:concrete-instances-finiteobservationbudgetselector-namecert} can consume the same finite request-to-tail-window route without importing data outside the accepted packet.
\end{theorem}
\begin{proof}
Start from the tail-realization factorization in \autoref{thm:regular-cauchy-modulus-realizer-tail-realization}. It already places every accepted Real or Completion precision request on the displayed route through $A,M,W,D,Q,E,H,C,P,N$, so a budget consumer reading the request has a finite carrier-facing spine before it reads any terminal seal.

Apply the request-transport determinacy of \autoref{thm:regular-cauchy-modulus-realizer-request-transport-determinacy}. If a $\RealObservationBudgetUp$ or $\FiniteObservationBudgetSelectorUp$ consumer serves the same request through the same displayed threshold replay, the selected window, tolerance ledger, readback, and terminal seal are the same classifier-facing downstream route.

It remains to exclude extra budget data. The carrier definition of \autoref{def:regular-cauchy-modulus-realizer-carrier} has no coordinate for an independent stream representative, hidden schedule, selected limit, quotient equality, countable-choice row, trichotomy row, or ambient completeness datum. The sibling budget consumers therefore receive only the finite route exposed by $R$ and its structural rows.
\end{proof}

\begin{theorem}[Regular Cauchy modulus realizer Real seal nonescape]
\label{thm:regular-cauchy-modulus-realizer-nonescape}
Let $R=(A,M,W,D,Q,E,H,C,P,N)$ be an accepted $\RegularCauchyModulusRealizerUp$ carrier. Any downstream use of the terminal $\RealUp$ seal $E$ must pass through the precision request row, Cauchy-modulus threshold, selected finite tail window, dyadic tolerance ledger, regular rational readback, and structural rows of the same carrier. Thus the seal cannot be used as a hidden endpoint for Real completeness, quotient stream equality, host real equality, countable choice, a selected limit, trichotomy, open-cover compactness, Lean verification, or a standard bridge.
\end{theorem}
\begin{proof}
Use the tail-realization route of \autoref{thm:regular-cauchy-modulus-realizer-tail-realization}. It places $E$ after $A,M,W,D,Q$, so every accepted seal read is attached to the displayed request, threshold, window, tolerance, and readback rows.

Now inspect the classifier surface of \autoref{def:regular-cauchy-modulus-realizer-carrier}. The carrier has no second Real-seal coordinate and no coordinate for completeness, quotient equality, host equality, choice, selected limits, trichotomy, open-cover compactness, Lean evidence, or bridge data.

Therefore a downstream read that bypasses one of $A,M,W,D,Q,H,C,P,N$ is not a read of the accepted carrier. The only available terminal route is the finite route named by $R$.
\end{proof}

\falsifiablePrediction{Every $\RegularCauchyModulusRealizerUp$ precision read factors through a request row, Cauchy-modulus threshold, finite StreamName tail window, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchy-realizer, realcauchymodulus, cauchymodulus, streamname, regseqrat, dyadicratcore, real: $\RegularCauchyModulusRealizerUp$ is not bijective to any listed sibling because it jointly carries request admission, threshold realization, finite tail-window selection, dyadic tolerance accounting, regular readback, terminal seal routing, transport, replay, provenance, and local naming.}

\closureat{RegularCauchyModulusRealizerUp}{seedStr}

\begin{closurestatus}{\RegularCauchyModulusRealizerUp}
  \constructivestory{A $\RegularCauchyModulusRealizerUp$ packet is generated from a precision request row, a Cauchy-modulus threshold row, a selected finite StreamName tail window, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-modulus-realizer-carrier}, \autoref{thm:regular-cauchy-modulus-realizer-namecert-obligations}, \autoref{thm:regular-cauchy-modulus-realizer-tail-realization}, \autoref{thm:regular-cauchy-modulus-realizer-request-transport-determinacy}, \autoref{thm:regular-cauchy-modulus-realizer-selector-budget-exhaustion}, and \autoref{thm:regular-cauchy-modulus-realizer-nonescape} seed the finite request-to-tail-window realization route for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient stream equality, host real equality, countable choice, selected limits, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, request admission, threshold realization, tail-window selection, tolerance accounting, readback and seal routing, tail realization, and Real-seal non-escape for BEDC.Derived.RegularCauchyModulusRealizerUp.}
\end{closurestatus}
