\chapter{A Concrete Naming Certificate for $\NestedIntervalRealUp$}
\label{ch:concrete-instances-nested-interval-real-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\NestedIntervalRealUp$ packet records the classical nested located interval route to a real name as finite BEDC data. It sits after the located interval carrier of \autoref{ch:concrete-instances-located-real-interval-namecert}, the bisection route of \autoref{ch:concrete-instances-located-interval-bisection-namecert}, the dyadic refinement surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the nested dyadic Cauchy route of \autoref{ch:concrete-instances-nested-dyadic-cauchy-namecert}, the finite $\StreamNameUp$ windows of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only the displayed interval-nest route; it is not open-cover compactness, countable choice, quotient real equality, selected-limit data, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[NestedIntervalReal carrier]
\label{def:nested-interval-real-carrier}
A $\NestedIntervalRealUp$ carrier is a finite $\BHist$ packet
$$
J=(I,B,D,E,W,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite family of nested $\LocatedRealIntervalUp$ rows whose endpoints, radii, locators, and metric brackets are visible to the packet.
\item $B$ is the $\LocatedIntervalBisectionUp$ refinement ledger, recording how each displayed interval row narrows to the next row.
\item $D$ is the $\DyadicRatCoreUp$ diameter-decay ledger, assigning to each displayed stage a dyadic bound whose carrier proves that later intervals have diameter at most the requested tolerance.
\item $E$ records the endpoint $\RealUp$ seals for all displayed interval endpoints and states that endpoint reads are available only through the interval rows in $I$.
\item $W$ is the finite $\StreamNameUp$ window family opened for the midpoint, left-endpoint, right-endpoint, and diameter observations used by the nest.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from $W,D,E$, so every rational approximation is sourced by a displayed window and a dyadic diameter bound.
\item $S$ is the terminal $\RealUp$ seal reached by the nested interval route after $I,B,D,E,W,R$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the interval rows, bisection ledger, diameter ledger, endpoint seals, stream windows, regular readback, terminal seal, replay, provenance, and local naming data.
\item $C$ records displayed $\Cont$ replay for consumers that inspect the interval nest, the dyadic diameter decay, the regular readback, or the terminal seal.
\item $P$ is the $\Pkg$ provenance over $\NestedIntervalRealUp$, $\LocatedRealIntervalUp$, $\LocatedIntervalBisectionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedIntervalRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,B,D,E,W,R,S,H,C,P,N$. It has no coordinate for arbitrary open covers, a countable selector, a quotient construction of reals, selected limiting points, host real equality, or a proof that $\RealUp$ is complete.
\end{definition}
\leanchecked{BEDC.Derived.NestedIntervalRealUp.TasteGate.NestedIntervalRealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[NestedIntervalReal NameCert obligations]
\label{thm:nested-interval-real-namecert-obligations}
For every accepted $\NestedIntervalRealUp$ carrier
$$
J=(I,B,D,E,W,R,S,H,C,P,N),
$$
the local $\NameCert_{\NestedIntervalRealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located interval rows, bisection ledger, dyadic diameter-decay ledger, endpoint seals, stream windows, regular readback, terminal seal, transports, replay, provenance, and local naming;
\item nesting exactness, requiring every later interval read to factor through the previous interval row and the displayed $\LocatedIntervalBisectionUp$ refinement in $B$;
\item diameter decay, requiring every requested tolerance to be witnessed by a dyadic bound in $D$ and by endpoint seals in $E$ before the regular readback row is exposed;
\item readback ordering, requiring $\StreamNameUp$ windows in $W$ and $\RegSeqRatUp$ readback in $R$ to be replayed before the terminal $\RealUp$ seal $S$ is available;
\item classifier stability, requiring transported packets to compare only through the stored $\hsame$ and $\Cont$ rows;
\item ledger non-escape, requiring $P,N$ to source and name no open-cover compactness, countable choice, selected limit, host real equality, quotient real construction, or $\RealUp$ completeness theorem.
\end{enumerate}
No nested-interval real obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:nested-interval-real-carrier}. The accepted packet displays exactly one interval-nest family, one bisection ledger, one dyadic diameter ledger, one endpoint-seal row, one finite window family, one regular readback row, one terminal real seal, and the structural rows that transport, replay, package, and name them.

Nesting exactness is read from $I$ and $B$. The only way to pass from one interval stage to the next is the displayed bisection row, so a consumer cannot substitute an external interval selection rule for the stored refinement ledger.

Diameter decay is read from $D$ together with the endpoint seals $E$. For a requested tolerance, the packet first displays the dyadic bound and then opens only the endpoint reads attached to the corresponding interval rows.

The readback route is downstream of those rows. Stream windows in $W$ expose finite observations, the $\RegSeqRatUp$ row $R$ packages them as regular rational readback, and the $\RealUp$ seal $S$ is reached only after that readback is replayed.

Finally, $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier contains no open-cover, choice, selected-limit, host-equality, quotient-construction, or real-completeness coordinate, none of those objects can enter the local NameCert surface.
\end{proof}

\begin{theorem}[NestedIntervalReal Cauchy selection route]
\label{thm:nested-interval-real-cauchy-selection}
For every accepted $\NestedIntervalRealUp$ carrier $J=(I,B,D,E,W,R,S,H,C,P,N)$ and every displayed precision request, the exported rational approximation is valid only through the staged finite obligation
$$
D_{\mathrm{diam}} \longrightarrow B_{\mathrm{path}} \longrightarrow E_{\mathrm{end}} \longrightarrow W_{\mathrm{win}} \longrightarrow R_{\mathrm{reg}} \longrightarrow S .
$$
That is, the packet must first exhibit a stage row whose dyadic diameter entry in $D$ is below the requested tolerance, then exhibit through $B$ the bisection path from the earlier interval rows in $I$ to that stage, then read the endpoint seals through $E$, then open only the corresponding finite $\StreamNameUp$ windows in $W$, then package the resulting rational approximation by the $\RegSeqRatUp$ readback row $R$, and only then expose the terminal $\RealUp$-facing seal $S$. The approximation is therefore a displayed regular-readback product of the carrier rows, not a point chosen from an ambient intersection.
\end{theorem}
\begin{proof}
Project the accepted carrier and fix a displayed precision request. The diameter ledger $D$ supplies the tolerance witness: a finite stage row whose dyadic diameter entry is below the requested bound.

The stage is reachable only through the stored interval data. The rows in $I$ display the located interval family, and the bisection ledger $B$ records the finite path from earlier intervals to the chosen stage, so the construction has no separate selection rule for later intervals.

Endpoint access is then ordered through $E$. The candidate rational approximation is read from endpoint seals attached to the same displayed stage, not from a host real point or an unrecorded intersection element.

Regular readback begins only after those seals have been fixed. The finite observations pass through the matching $\StreamNameUp$ windows in $W$, and the $\RegSeqRatUp$ row $R$ packages the resulting rational read as the Cauchy-facing approximation.

Finally, $S$ seals exactly that read for the $\RealUp$-facing consumer. The transport, replay, provenance, and local naming rows $H,C,P,N$ preserve the staged route under comparison and replay, so no ambient intersection point, choice-selected subsequence, quotient representative, or independent completeness theorem is used to obtain the approximation.
\end{proof}

\begin{theorem}[NestedIntervalReal tail-modulus readback]
\label{thm:nested-interval-real-tail-modulus-readback}
For every accepted $\NestedIntervalRealUp$ carrier
$$
J=(I,B,D,E,W,R,S,H,C,P,N)
$$
and every displayed precision request whose dyadic diameter witness is read from $D$, the request determines a finite tail-modulus readback route
$$
D \longrightarrow W \longrightarrow R \longrightarrow S .
$$
The diameter row supplies the requested tolerance bound, the matching $\StreamNameUp$ windows in $W$ expose only the finite observations at that bound, the $\RegSeqRatUp$ row $R$ packages those observations as the regular rational readback, and the terminal $\RealUp$ seal $S$ consumes exactly that readback. Thus the modulus exported to the regular rational surface is a displayed BEDC obligation of $J$, not an independent completeness or intersection principle.
\end{theorem}
\begin{proof}
Project the accepted carrier $J$. By \autoref{thm:nested-interval-real-cauchy-selection}, a displayed precision request is already ordered by the staged finite route from the diameter ledger to the terminal seal. In particular, the dyadic entry in $D$ is the row that fixes the requested tail bound before any regular readback is exposed.

Once that bound is fixed, the only observations available at the bound are the corresponding finite $\StreamNameUp$ windows in $W$. The carrier definition in \autoref{def:nested-interval-real-carrier} gives no coordinate for an independent selector, ambient intersection point, or external modulus source, so the request can only continue through the rows already displayed by $J$.

The $\RegSeqRatUp$ row $R$ then repackages exactly those finite window observations as the regular rational readback. The terminal $\RealUp$ seal $S$ is downstream of $R$ in the carrier and in the staged route, so it consumes that readback rather than a separately chosen real point. Therefore the tail-modulus readback is the finite BEDC obligation
$$
D \longrightarrow W \longrightarrow R \longrightarrow S
$$
inside the packet.
\end{proof}

\begin{theorem}[NestedIntervalReal ledger nonescape]
\label{thm:nested-interval-real-ledger-nonescape}
For an accepted $\NestedIntervalRealUp$ carrier $J=(I,B,D,E,W,R,S,H,C,P,N)$, every $\RealUp$-facing, $\RegSeqRatUp$-facing, or interval-facing read exported by $J$ is generated by the rows named in \autoref{def:nested-interval-real-carrier}. In particular, the packet exports no open-cover compactness principle, countable-choice selector, selected limit, host real equality, quotient construction of reals, or proof of $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. An interval-facing read must pass through $I,B,D,E$, because these are the only rows that contain located interval data, bisection refinement, dyadic diameter decay, and endpoint seals.

A $\RegSeqRatUp$-facing read must pass through $W$ and $R$. These are the only finite window and regular readback rows available to the packet.

A $\RealUp$-facing read must then pass through $S$, and any comparison of two accepted packets must use $H$ and $C$ before $P$ and $N$ can record provenance and local naming.

Thus every exported read is generated by the displayed ledger. The excluded compactness, choice, selected-limit, host-equality, quotient-construction, and completeness objects are absent from the carrier and cannot be produced by projection, transport, replay, provenance, or local naming.
\end{proof}

\closureat{NestedIntervalRealUp}{seedStr}

\begin{closurestatus}{\NestedIntervalRealUp}
  \constructivestory{A $\NestedIntervalRealUp$ packet is generated from nested located interval rows, a located-bisection refinement ledger, dyadic diameter-decay rows, endpoint $\RealUp$ seals, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-interval-real-carrier}, \autoref{thm:nested-interval-real-namecert-obligations}, \autoref{thm:nested-interval-real-cauchy-selection}, \autoref{thm:nested-interval-real-tail-modulus-readback}, and \autoref{thm:nested-interval-real-ledger-nonescape} seed the finite nested located interval route from diameter-decaying intervals to regular rational readback and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, countable choice, selected limits, host real equality, quotient construction, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nesting exactness, diameter decay, endpoint-seal ordering, Cauchy selection routing, classifier stability, and ledger non-escape for BEDC.Derived.NestedIntervalRealUp.}
\end{closurestatus}
