\chapter{A Concrete Naming Certificate for $\DoubleLimitInterchangeUp$}
\label{ch:concrete-instances-double-limit-interchange-namecert}
\origin{human}

Following Bishop and Bridges, the $\DoubleLimitInterchangeUp$ packet records a finite certificate for exchanging two Cauchy limit routes through displayed windows rather than through an ambient completeness principle. Its dependency surface is the $\StreamNameUp$ schedule interface of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the shared dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the diagonal-route discipline of \autoref{ch:concrete-instances-cauchy-diagonal-limit-namecert}, the uniform-window route of \autoref{ch:concrete-instances-uniform-limit-interchange-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The packet records a boundary for exchanging two displayed completion-facing reads; it does not claim selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Double-limit interchange carrier]
\label{def:double-limit-interchange-carrier}
A $\DoubleLimitInterchangeUp$ carrier is a finite $\BHist$ packet
$$
I=(O,J,D,\Delta,R_0,R_1,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the outer $\StreamNameUp$ schedule, listing the finite outer windows inspected by a completion-facing consumer.
\item $J$ is the inner $\StreamNameUp$ schedule, listing the finite inner windows read under each displayed outer window.
\item $D$ is the shared $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic request, the two Cauchy-window budgets, and the comparison margin used by both routes.
\item $\Delta$ is the diagonal selector row supplied through the $\CauchyDiagonalLimitUp$ route, choosing a displayed common window only from $O,J,D$.
\item $R_0$ is the first $\RegSeqRatUp$ readback, obtained by reading the outer schedule before the inner schedule and then applying the shared dyadic ledger.
\item $R_1$ is the second $\RegSeqRatUp$ readback, obtained by reading the inner schedule before the outer schedule and then applying the same shared dyadic ledger.
\item $E$ is the terminal $\RealUp$ seal row for the common displayed Cauchy-window read.
\item $H$ records componentwise $\hsame$ transport for the outer schedule, inner schedule, dyadic ledger, diagonal selector, first readback, second readback, real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any requested precision through $O,J,D,\Delta,R_0,R_1,E$.
\item $P$ is the $\Pkg$ provenance over $\DoubleLimitInterchangeUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyDiagonalLimitUp$, $\UniformLimitInterchangeUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DoubleLimitInterchangeUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It has no coordinate for selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.DoubleLimitInterchangeUp.DoubleLimitInterchangeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Double-limit interchange NameCert obligations]
\label{thm:double-limit-interchange-namecert-obligations}
For every accepted $\DoubleLimitInterchangeUp$ carrier
$$
I=(O,J,D,\Delta,R_0,R_1,E,H,C,P,N),
$$
the local $\NameCert_{\DoubleLimitInterchangeUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed outer schedule, inner schedule, shared dyadic tolerance ledger, diagonal selector, first readback, second readback, real seal, transport, continuation, provenance, and local naming row;
\item shared-window routing, requiring every route comparison to expose $O,J,D$ before either $\RegSeqRatUp$ readback row is available;
\item diagonal routing, requiring the selector $\Delta$ to be read through the $\CauchyDiagonalLimitUp$ packet before any common real seal can be consumed;
\item uniform interchange routing, requiring both readback directions $R_0$ and $R_1$ to use the same dyadic tolerance ledger and the same displayed windows, as in the $\UniformLimitInterchangeUp$ route;
\item structural stability, requiring $H$ and $C$ to transport and replay only the displayed rows, with provenance supplied by $P$ and local naming supplied by $N$.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:double-limit-interchange-carrier}. The displayed coordinates are exactly the two schedules, the shared dyadic tolerance ledger, the diagonal selector, the two regular readbacks, the real seal, the structural transport and replay rows, provenance, and the local name.

The route comparison first exposes the schedules and the shared tolerance. Since both readback rows are downstream of $O,J,D$, a consumer cannot replace one side by a separately chosen window or tolerance.

The diagonal selector supplies the common Cauchy window. It is read through the same finite diagonal route used by $\CauchyDiagonalLimitUp$, so it cannot introduce a selected limit or a quotient-stream representative.

The interchange step then reads $R_0$ and $R_1$ through the uniform-window discipline of $\UniformLimitInterchangeUp$. The two orders of reading are admitted only as two routes through the same displayed rows.

Finally $H,C,P,N$ transport, replay, source, and name that finite surface. These structural rows add no analytic coordinate, so the listed obligations exhaust the local certificate.
\end{proof}

\begin{theorem}[Double-limit interchange diagonal route]
\label{thm:double-limit-interchange-diagonal-route}
Every $\RealUp$-facing read of an accepted $\DoubleLimitInterchangeUp$ carrier factors through the finite route
$$
O,J,D \longmapsto \Delta \longmapsto (R_0,R_1) \longmapsto E
$$
and then through the stored $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$. The two orders of Cauchy-window readback therefore meet at a displayed diagonal selector and a shared dyadic tolerance ledger; the route exports no selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a real-facing precision request. Carrier admission gives the request only the outer schedule $O$, the inner schedule $J$, and the shared dyadic tolerance ledger $D$.

The diagonal row $\Delta$ is the next available common-window object. It is computed from the displayed schedules and tolerance ledger, matching the diagonal route supplied by \autoref{ch:concrete-instances-cauchy-diagonal-limit-namecert}.

The two readbacks $R_0$ and $R_1$ are then read through the same finite window data. The first uses the outer-then-inner order and the second uses the inner-then-outer order, but both consume the same $O,J,D,\Delta$ surface.

The terminal seal $E$ is downstream of those readbacks. After $E$, the rows $H,C,P,N$ only transport, replay, source, and name the route. Since no excluded analytic object occurs in the carrier inventory, the real-facing read cannot leave the displayed path.
\end{proof}

\begin{theorem}[Double-limit interchange nonescape]
\label{thm:double-limit-interchange-nonescape}
Every public read of an accepted $\DoubleLimitInterchangeUp$ carrier is exhausted by the rows $O,J,D,\Delta,R_0,R_1,E,H,C,P,N$. In particular, the packet cannot export selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. The analytic rows are the two stream schedules, the shared dyadic tolerance ledger, the diagonal selector, the two regular readbacks, and the terminal real seal.

The remaining rows are structural. Transport $H$ preserves componentwise classifier data, continuation $C$ replays displayed precision routes, provenance $P$ records the sibling sources, and $N$ supplies the local certificate row.

There is no coordinate left for selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, or ambient completeness. Therefore every public read is confined to the finite packet.
\end{proof}

\closureat{DoubleLimitInterchangeUp}{seedStr}

\begin{closurestatus}{\DoubleLimitInterchangeUp}
  \constructivestory{A $\DoubleLimitInterchangeUp$ packet is generated from an outer StreamName schedule, an inner StreamName schedule, a shared DyadicRatCore tolerance ledger, a CauchyDiagonalLimit selector, two RegSeqRat readbacks, a RealUp seal, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:double-limit-interchange-carrier}, \autoref{thm:double-limit-interchange-namecert-obligations}, \autoref{thm:double-limit-interchange-diagonal-route}, and \autoref{thm:double-limit-interchange-nonescape} seed the double-limit interchange packet over stream schedules, regular readbacks, dyadic tolerance rows, diagonal selection, uniform interchange routing, and RealUp seal descent.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, host function equality, quotient streams, countable choice, trichotomy, open-cover compactness, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, shared-window routing, diagonal routing, uniform interchange routing, structural stability, and nonescape for BEDC.Derived.DoubleLimitInterchangeUp.}
\end{closurestatus}
