\chapter{A Concrete Naming Certificate for $\FejerKernelUp$}
\label{ch:concrete-instances-fejer-kernel-namecert}
\origin{human}

Following Fejer's positive summability kernels and the classical accounts of Zygmund and Katznelson, the $\FejerKernelUp$ packet records the finite Fourier kernel that averages symmetric coefficient windows before any constructive approximation theorem consumes a uniform-limit handoff. It sits over the finite Fourier observation interface of \autoref{ch:concrete-instances-fourier-namecert}, the circle source of \autoref{ch:concrete-instances-s1-namecert}, the real-analytic trigonometric rows of \autoref{ch:concrete-instances-real-analytic-namecert}, the normalization route of \autoref{ch:concrete-instances-integral-namecert}, and the approximation-facing boundary of \autoref{ch:concrete-instances-uniformlimit-namecert}. The chapter names a positive finite kernel object; it does not import Haar measure, quotient function spaces, host Fourier convergence, or a completed approximation theorem.

\begin{definition}[Fejer kernel carrier]\label{def:fejer-kernel-carrier}
A $\FejerKernelUp$ carrier is a finite $\BHist$ packet
$$
K=(F,S,A,I,U,P,T,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FourierUp$ coefficient-window row, recording the symmetric window, triangular weights, endpoint truncation bound, and finite coefficient probes used by the kernel.
\item $S$ is the $\SOneUp$ phase-sample row, exposing only displayed circle samples and their componentwise classifier data.
\item $A$ is the $\RealAnalyticUp$ sine/cosine polynomial row, presenting the trigonometric polynomial determined by $F$ and $S$ as finite real-analytic algebra data.
\item $I$ is the $\IntegralUp$ normalization witness, recording the displayed integral row that makes the kernel total mass equal to the certified unit.
\item $U$ is the $\UniformLimitUp$ handoff row available to later approximation packets after the finite kernel and its normalization have been exposed.
\item $P$ is the positivity ledger, listing the square-modulus presentation, nonnegative coefficient witnesses, finite averaging denominator, and nonnegative-kernel stability entries used by the carrier.
\item $T$ records componentwise $\hsame$ transport for coefficient windows, phase samples, trigonometric polynomial rows, integral witnesses, uniform-limit handoff rows, positivity ledgers, continuation replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a phase and coefficient-window request through $F,S,A,P$, then through $I$ to the normalized kernel and through $U$ to the approximation-facing handoff.
\item $Q$ is the $\Pkg$ provenance over $\FejerKernelUp$, $\FourierUp$, $\SOneUp$, $\RealAnalyticUp$, $\IntegralUp$, $\UniformLimitUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FejerKernelUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,S,A,I,U,P,T,C,Q,N$. It has no coordinate for Haar measure, an ambient quotient of functions, host-level almost-everywhere equality, or an external Fourier convergence principle.
\end{definition}

\begin{theorem}[Fejer kernel NameCert obligations]\label{thm:fejer-kernel-namecert-obligations}
For every accepted $\FejerKernelUp$ carrier $K=(F,S,A,I,U,P,T,C,Q,N)$, the local $\NameCert_{\FejerKernelUp}$ surface consists exactly of the following five finite rows:
\begin{enumerate}
\item carrier admission for the displayed Fourier coefficient-window, circle phase-sample, real-analytic polynomial, integral-normalization, uniform-limit handoff, positivity-ledger, transport, continuation, provenance, and naming rows;
\item classifier transport, requiring $\hsame$ comparison to move componentwise through $F,S,A,I,U,P,T,C,Q,N$ without replacing the displayed finite kernel by host function equality;
\item finite positivity and nonnegative-kernel stability, requiring the square-modulus presentation and triangular-weight ledger in $P$ to be preserved by the displayed finite algebra rows;
\item integral-normalization handoff, requiring the unit-mass witness in $I$ to be read before any $\UniformLimitUp$ approximation consumer receives the handoff row $U$;
\item ledger non-escape, requiring every coefficient window, phase sample, sine/cosine polynomial row, normalization witness, positivity entry, transport row, continuation replay, and provenance row to remain inside the same finite packet.
\end{enumerate}
These obligations certify a positive finite summability kernel over the named source rows, not a host convergence theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:fejer-kernel-carrier}. Carrier admission is exactly the finite inventory $F,S,A,I,U,P,T,C,Q,N$, so the certificate has no hidden coordinate for a completed function space, a Haar-measure object, or an external convergence theorem.

Classifier transport is componentwise. The $\FourierUp$ row transports coefficient windows, the $\SOneUp$ row transports phase samples, the $\RealAnalyticUp$ row transports the sine/cosine polynomial data, the $\IntegralUp$ row transports the normalization witness, and the $\UniformLimitUp$ row transports only the handoff exposed by the earlier rows.

The positivity clause is read from the displayed ledger $P$. The square-modulus presentation and triangular weights are finite trigonometric-polynomial algebra data, so nonnegativity is stable under the same componentwise transport that preserves $F,S,A$.

The integral-normalization handoff is then forced through $I$. A later approximation packet may read $U$ only after the normalization row has displayed the unit-mass witness for the same finite kernel.

Finally, $T,C,Q,N$ preserve, replay, source, and name exactly the displayed route. Since every analytic datum used by the kernel has already appeared in the carrier rows, the ledger cannot be used to recover an unrecorded measure, quotient, or convergence principle.
\end{proof}

\falsifiablePrediction{Every $\FejerKernelUp$ approximation-facing read factors through Fourier coefficient windows, SOne phase samples, RealAnalytic sine/cosine polynomial rows, an Integral normalization witness, a UniformLimit handoff, a positivity ledger, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{fourier, s1, real-analytic, integral, uniformlimit: $\FejerKernelUp$ is not bijective to any listed sibling because it jointly carries triangular Fourier coefficient windows, circle phase samples, real-analytic trigonometric polynomial rows, integral normalization, uniform-limit handoff, positivity ledger, transport, replay, provenance, and local naming.}

\closureat{FejerKernelUp}{seedStr}

\begin{closurestatus}{\FejerKernelUp}
  \constructivestory{A $\FejerKernelUp$ packet is generated from finite Fourier coefficient windows with triangular weights, displayed $\SOneUp$ phase samples, $\RealAnalyticUp$ sine/cosine polynomial rows, an $\IntegralUp$ normalization witness, a $\UniformLimitUp$ handoff row, a positivity ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fejer-kernel-carrier} and \autoref{thm:fejer-kernel-namecert-obligations} seed the finite positive summability-kernel route from Fourier coefficient windows to constructive approximation-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Haar measure, quotient function spaces, host Fourier convergence, pointwise convergence, uniform convergence of Fourier means, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, finite positivity stability, integral-normalization handoff, ledger non-escape, and TasteGate field faithfulness for BEDC.Derived.FejerKernelUp.}
\end{closurestatus}
