\chapter{A Concrete Naming Certificate for $\RegularCauchyModulusStabilityUp$}
\label{ch:concrete-instances-regular-cauchy-modulus-stability-namecert}
\origin{human}

Following Bishop and Bridges constructive Cauchy sequence discipline, the $\RegularCauchyModulusStabilityUp$ packet records the finite transport surface by which a displayed regular Cauchy modulus remains usable after tail-equivalent regular names are presented to Real and Completion consumers. It sits over the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the request-to-window route of \autoref{ch:concrete-instances-regular-cauchy-modulus-realizer-namecert}. The packet is a finite stability certificate for reusing a Cauchy modulus across a displayed tail-equivalence route; it is not quotient stream equality, selected limit data, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.

\begin{definition}[Regular Cauchy modulus stability carrier]
\label{def:regular-cauchy-modulus-stability-carrier}
A $\RegularCauchyModulusStabilityUp$ carrier is a finite $\BHist$ packet
$$
S=(A,B,M,T,W_A,W_B,D_A,D_B,Q_A,Q_B,E_A,E_B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two $\RegSeqRatUp$ source rows whose finite regular Cauchy observations are related by a displayed tail-equivalence route.
\item $M$ is the reusable Cauchy-modulus row, read through the $\RegularCauchyModulusRealizerUp$ request-to-window surface.
\item $T$ is the finite tail-equivalence ledger, recording the cutoff, paired tail windows, and rowwise agreement evidence that allows the same modulus request to be read from either source after the cutoff.
\item $W_A$ and $W_B$ are the $\StreamNameUp$ tail-window rows selected from $A$ and $B$ by the request, the reusable modulus row $M$, and the ledger $T$.
\item $D_A$ and $D_B$ are the $\DyadicRatCoreUp$ tolerance ledgers attached to the two selected tail windows.
\item $Q_A$ and $Q_B$ are the $\RegSeqRatUp$ readback rows obtained from the selected windows and dyadic ledgers.
\item $E_A$ and $E_B$ are the terminal $\RealUp$ seal rows reached only after the source, modulus, tail-equivalence, window, tolerance, and readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source rows, reusable modulus, tail-equivalence ledger, selected windows, tolerance ledgers, readbacks, real seals, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from every Real or Completion request through $M,T,W_A,W_B,D_A,D_B,Q_A,Q_B,E_A,E_B$ and then through $H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyModulusStabilityUp$, $\RegularCauchyModulusRealizerUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyModulusStabilityUp}$ row.
\end{enumerate}
The classifier compares accepted stability packets only through the displayed rows $A,B,M,T,W_A,W_B,D_A,D_B,Q_A,Q_B,E_A,E_B,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyModulusStabilityUp.RegularCauchyModulusStabilityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy modulus stability NameCert obligations]
\label{thm:regular-cauchy-modulus-stability-namecert-obligations}
For every accepted $\RegularCauchyModulusStabilityUp$ carrier
$$
S=(A,B,M,T,W_A,W_B,D_A,D_B,Q_A,Q_B,E_A,E_B,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyModulusStabilityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the source rows $A,B$, reusable modulus $M$, tail-equivalence ledger $T$, selected windows $W_A,W_B$, tolerance ledgers $D_A,D_B$, readbacks $Q_A,Q_B$, real seals $E_A,E_B$, and structural rows $H,C,P,N$;
\item modulus admission, requiring every transported precision request to read the displayed modulus row $M$ before either tail window is selected;
\item tail-equivalence exactness, requiring $T$ to store the cutoff and paired tail-window agreement used for the two sources;
\item window selection, requiring $W_A$ and $W_B$ to be selected from the same request and the same modulus row, with $T$ supplying only the tail-alignment data;
\item dyadic accounting, requiring $D_A$ and $D_B$ to store exactly the tolerance radii and slack comparisons consumed by their corresponding selected windows;
\item readback and seal routing, requiring $Q_A,E_A$ and $Q_B,E_B$ to remain downstream of their matching source, window, and dyadic ledger;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$;
\item non-escape for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, and standard-bridge data.
\end{enumerate}
No regular Cauchy modulus stability obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-modulus-stability-carrier}. The only analytic coordinates are the two sources $A,B$, the reusable modulus $M$, the tail-equivalence ledger $T$, the two selected windows, the two dyadic ledgers, the two readbacks, and the two terminal seals.

The modulus route is forced before any branch read. A Real or Completion request first reads $M$, and the selected tail windows $W_A,W_B$ are then formed from the same request together with the tail-equivalence ledger $T$.

The ledger $T$ contributes only the finite cutoff and paired tail-window agreement evidence. It does not identify the streams as quotient objects and does not select a limiting real.

The dyadic, readback, and seal rows remain branchwise. The rows $D_A,Q_A,E_A$ are downstream of $A,W_A$, and the rows $D_B,Q_B,E_B$ are downstream of $B,W_B$.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed finite route. Since none of the excluded objects appears as a coordinate, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Regular Cauchy modulus stability tail-equivalence transport]
\label{thm:regular-cauchy-modulus-stability-tail-equivalence-transport}
Let
$$
S=(A,B,M,T,W_A,W_B,D_A,D_B,Q_A,Q_B,E_A,E_B,H,C,P,N)
$$
be an accepted $\RegularCauchyModulusStabilityUp$ carrier. Every Real or Completion request that uses the reusable modulus $M$ on the $A$ source has a transported finite route on the $B$ source through the same modulus row, the displayed tail-equivalence ledger, the selected $B$-window, the $B$-side dyadic ledger, the $B$-side readback, and the $B$-side real seal. Conversely, every $B$-side routed request transports back through the displayed $A$-side rows. The transport supplies reuse of the modulus across tail-equivalent regular names without quotient equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean evidence, or standard-bridge data.
\end{theorem}
\begin{proof}
Start with an $A$-side request. By \autoref{thm:regular-cauchy-modulus-stability-namecert-obligations}, the request reads $M$ before any selected window is consumed.

Use the tail-equivalence ledger $T$. It records the finite cutoff and paired tail-window agreement rows, so the same request and modulus row select the $B$-side window $W_B$ whenever the $A$-side route has selected $W_A$ beyond the cutoff.

The transported branch then reads $D_B$, $Q_B$, and $E_B$ in order. These rows are the only $B$-side tolerance, readback, and seal coordinates in the carrier, so the transported route has no additional branch or hidden endpoint.

The reverse direction is symmetric. Begin with the $B$-side route, read the same modulus row $M$, use the same ledger $T$ to recover the paired $A$-side window $W_A$, and then pass through $D_A,Q_A,E_A$.

The structural rows $H,C,P,N$ record both directions as componentwise transport and displayed replay over the same finite packet. Thus the carrier transports the reusable modulus across the displayed tail-equivalence surface and introduces none of the excluded quotient, selector, choice, equality, order, completeness, verification, or bridge objects.
\end{proof}

\falsifiablePrediction{Every $\RegularCauchyModulusStabilityUp$ Real or Completion read that reuses a Cauchy modulus across tail-equivalent regular names factors through two RegSeqRat source rows, one reusable RegularCauchyModulusRealizer route, a finite tail-equivalence ledger, paired StreamName tail windows, paired DyadicRatCore tolerance ledgers, paired RegSeqRat readbacks, paired RealUp seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{regular-cauchy-modulus-realizer, regseqrat, streamname, dyadicratcore, real: $\RegularCauchyModulusStabilityUp$ is not bijective to any listed sibling because it jointly carries two source rows, one reusable modulus row, a tail-equivalence ledger, paired selected windows, paired tolerance ledgers, paired readbacks, paired terminal seals, transport, replay, provenance, and local naming.}

\closureat{RegularCauchyModulusStabilityUp}{seedStr}

\begin{closurestatus}{\RegularCauchyModulusStabilityUp}
  \constructivestory{A $\RegularCauchyModulusStabilityUp$ packet is generated from two RegSeqRat source rows, one reusable RegularCauchyModulusRealizer route, a finite tail-equivalence ledger, paired StreamName tail windows, paired DyadicRatCore tolerance ledgers, paired RegSeqRat readbacks, paired RealUp seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-modulus-stability-carrier}, \autoref{thm:regular-cauchy-modulus-stability-namecert-obligations}, and \autoref{thm:regular-cauchy-modulus-stability-tail-equivalence-transport} seed the finite modulus-transport route for tail-equivalent regular names consumed by L10 Real and Completion interfaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, modulus admission, tail-equivalence exactness, window selection, dyadic accounting, readback and seal routing, and tail-equivalence transport for BEDC.Derived.RegularCauchyModulusStabilityUp.}
\end{closurestatus}
