\chapter{A Concrete Naming Certificate for $\CauchyCompletionFunctorialityUp$}
\label{ch:concrete-instances-cauchy-completion-functoriality-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and Mac Lane's functorial language, the $\CauchyCompletionFunctorialityUp$ packet records the finite BEDC surface by which a uniformly continuous map between displayed sources induces a map between their Cauchy-completion seals. It reads the unit route of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the adjunction ledger of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert}, the extension handoff of \autoref{ch:concrete-instances-uniform-continuous-extension-namecert}, and the separated uniqueness boundary of \autoref{ch:concrete-instances-completion-extension-uniqueness-namecert}. The chapter names only the finite NameCert boundary for this functorial action; it does not identify quotient completions, choose representatives, or assert host equality of completed spaces.

\begin{definition}[CauchyCompletionFunctoriality carrier]
\label{def:cauchy-completion-functoriality-carrier}
A $\CauchyCompletionFunctorialityUp$ carrier is a finite $\BHist$ packet
$$
F=(S,T,f,E,U,I,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source completion row, including the displayed source object, its Cauchy-completion seal, and the unit route consumed before any completed read is available.
\item $T$ is the target completion row, including the displayed target object, its Cauchy-completion seal, and the matching unit route.
\item $f$ is the uniformly continuous source-map row, carrying the finite modulus and graph evidence used before completion-facing extension.
\item $E$ is the $\UniformContinuousExtensionUp$ row that extends $f$ from the dense source route into the target completion seal.
\item $U$ is the $\CompletionExtensionUniquenessUp$ row comparing any two extension candidates after agreement on the dense source and target completion rows.
\item $I$ is the identity ledger, recording that the source identity map extends through the same unit and adjunction rows to the identity completed read.
\item $L$ is the composition ledger, recording that two composable source-map rows extend in the same order as their source-side composition.
\item $H$ records componentwise $\hsame$ transport for the source completion row, target completion row, source-map row, extension row, uniqueness row, identity ledger, composition ledger, replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay of the route
$$
S,T,f\longmapsto E\longmapsto U\longmapsto I,L .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionFunctorialityUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionAdjunctionUp$, $\UniformContinuousExtensionUp$, $\CompletionExtensionUniquenessUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionFunctorialityUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, countable choice, host equality of completed spaces, open-cover compactness, or completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.CauchyCompletionFunctorialityUp.CauchyCompletionFunctorialityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyCompletionFunctoriality NameCert obligations]
\label{thm:cauchy-completion-functoriality-namecert-obligations}
For every accepted $\CauchyCompletionFunctorialityUp$ carrier
$$
F=(S,T,f,E,U,I,L,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionFunctorialityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source completion row, target completion row, uniformly continuous source-map row, extension row, uniqueness row, identity ledger, composition ledger, componentwise transport, replay, provenance, and local naming row;
\item unit compatibility, requiring both completion rows to expose their dense source routes before an extended completed-map read is available;
\item extension exactness, requiring the row $E$ to be the only completion-facing route generated from the uniformly continuous source-map row $f$;
\item uniqueness determinacy, requiring any two extension candidates over the same dense route to be compared only through the row $U$;
\item identity replay, requiring the identity source-map row to pass through the same unit and adjunction rows before the identity completed read is named by $I$;
\item composition replay, requiring composable source-map rows to pass through the same extension and uniqueness surfaces before the composed completed read is named by $L$;
\item ledger non-escape, requiring $H,C,P,N$ to expose no quotient completion equality, selected representatives, countable-choice schedule, host equality of completed spaces, open-cover compactness, or completeness of $\RealUp$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-functoriality-carrier}. The accepted packet displays exactly the source completion row, target completion row, uniformly continuous source-map row, extension row, uniqueness row, identity ledger, composition ledger, and structural rows.

Unit compatibility is read from $S$ and $T$. Each completed read begins with the corresponding source-side unit route, so no completed-map row can be inspected before the dense source and target routes have been displayed.

Extension exactness is the projection to $f$ and $E$. The source map is uniformly continuous by the carried finite modulus and graph evidence, and the only completion-facing image row generated from it is the $\UniformContinuousExtensionUp$ surface named by $E$.

Uniqueness determinacy is the projection to $U$. When two candidates agree on the displayed dense source route and target completion route, the packet compares them through the separated completion-extension uniqueness surface rather than through host function equality.

Finally, identity and composition are finite replay obligations. The rows $I$ and $L$ reuse the same unit and adjunction coordinates already present in $S,T,E,U$, while $H,C,P,N$ preserve only those displayed coordinates under componentwise transport, replay, provenance, and local naming. Since no excluded principle is a carrier coordinate, the seven obligation rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[CauchyCompletionFunctoriality map route]
\label{thm:cauchy-completion-functoriality-map-route}
Let
$$
F=(S,T,f,E,U,I,L,H,C,P,N)
$$
be an accepted $\CauchyCompletionFunctorialityUp$ carrier. Every completed-map read induced by the uniformly continuous source-map row $f$ factors through the finite route
$$
S,T,f\longmapsto E\longmapsto U\longmapsto H,C,P,N .
$$
The route uses the existing uniform-continuous extension surface for existence and the completion-extension uniqueness surface for determinacy. It does not use quotient completion equality, selected representatives, countable choice, host equality of completed spaces, open-cover compactness, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Start with a completed-map consumer. Projection gives the source and target completion rows $S,T$ and the uniformly continuous source-map row $f$.

The map route then enters the extension surface. The row $E$ is the only coordinate that turns the source-map evidence into a completion-facing target read, so the consumer must pass through the $\UniformContinuousExtensionUp$ handoff before it can read the completed map.

Determinacy is supplied by $U$. If a second candidate is presented over the same dense source route and target completion row, the comparison is routed through $\CompletionExtensionUniquenessUp$ and not through equality of host functions or completed spaces.

Transport and naming close the finite route. The componentwise $\hsame$ ledger $H$, the displayed $\Cont$ replay $C$, the provenance row $P$, and the local naming row $N$ preserve the same map route and add no coordinate for any excluded completion or choice principle.
\end{proof}

\begin{theorem}[CauchyCompletionFunctoriality composition]
\label{thm:cauchy-completion-functoriality-composition}
For accepted $\CauchyCompletionFunctorialityUp$ carriers over composable uniformly continuous source-map rows, the completed read of the composite source map is named by replaying the same unit, adjunction, extension, and uniqueness rows used for the two component maps. The identity source map is named by the same replay with the identity ledger $I$, and the composite source map is named by the composition ledger $L$.
\end{theorem}
\begin{proof}
For identity, project the carrier and read the ledger $I$. The source identity row first passes through the unit route in the source completion row, then through the adjunction-facing completion route, and then through the extension row $E$. The uniqueness row $U$ identifies the resulting completed read with the identity completed read carried by $I$.

For composition, apply the same projection to the composable source-map rows. Each component map is extended through its own displayed $E$ row, and the composite source-map row is then extended through the same uniform-continuous extension surface. The ledger $L$ records that these two completion-facing routes are compared only by the shared completion-extension uniqueness row.

The componentwise transport row $H$ and replay row $C$ preserve the identity and composition ledgers under accepted carrier comparison. Provenance $P$ and local naming $N$ therefore expose a functorial completed-map surface without exporting quotient completion equality, selected representatives, countable choice, host equality of completed spaces, open-cover compactness, or completeness of $\RealUp$.
\end{proof}

\begin{closurestatus}{\CauchyCompletionFunctorialityUp}
  \constructivestory{A $\CauchyCompletionFunctorialityUp$ packet is generated from source and target completion rows, a uniformly continuous source-map row, a UniformContinuousExtension handoff, a CompletionExtensionUniqueness ledger, identity and composition ledgers, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-functoriality-carrier}, \autoref{thm:cauchy-completion-functoriality-namecert-obligations}, \autoref{thm:cauchy-completion-functoriality-map-route}, and \autoref{thm:cauchy-completion-functoriality-composition} seed the finite functorial action surface for Cauchy completion on uniformly continuous maps.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, countable choice, host equality of completed spaces, open-cover compactness, completeness of $\RealUp$, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, unit compatibility, extension exactness, uniqueness determinacy, identity replay, composition replay, and ledger non-escape for BEDC.Derived.CauchyCompletionFunctorialityUp.}
\end{closurestatus}
