\chapter{A Concrete Naming Certificate for $\RealityConstrainedApproximationTowerUp$}
\label{ch:concrete-instances-reality-constrained-approximation-tower-namecert}
\origin{ai}

The \RealityConstrainedApproximationTowerUp packet realizes the indexed approximation-tower discipline of \autoref{ch:visions-reality-constrained-approximation-towers} as a composite BEDC NameCert carrier. It sits after the observation reflection packet of \autoref{ch:concrete-instances-observationreflectionpacket-namecert}, the ontic-state packet of \autoref{ch:concrete-instances-onticstate-namecert}, the approximation carrier of \autoref{ch:concrete-instances-approximation-namecert}, the finite Cauchy approximation carrier of \autoref{ch:concrete-instances-finite-cauchy-approximation-namecert}, the Real approximation envelope of \autoref{ch:concrete-instances-realapproximationenvelope-namecert}, and the observer-filter budget selector of \autoref{ch:concrete-instances-observer-filter-budget-selector-namecert}. Those siblings provide observation readback, ontic-state naming, approximation rows, finite Cauchy windows, Real-facing envelope data, and selected observer budgets; this carrier binds them into one indexed reality-constrained tower without importing host equality, quotient reals, hidden limit selectors, or ambient completeness.
As an ai packet, it bundles observation reflection, ontic-state
naming, approximation, finite Cauchy approximation, Real-envelope, and
observer-budget surfaces into one indexed tower ledger.

\begin{definition}[Reality-constrained approximation-tower carrier]
\label{def:reality-constrained-approximation-tower-packet}
A \RealityConstrainedApproximationTowerUp carrier is a finite $\BHist$ packet
$$
T=(O,D,M,S,C,F,L,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the ontic source row naming the reality-facing source whose signatures are being approximated;
\item $D$ is the observation-data row, containing the finite admissible observations selected for the tower and the displayed observation-reflection readback;
\item $M$ is the model row, naming the visible mathematical model read from the observed source;
\item $S$ is the physical-signature row extracted from $O$ through $D$ and read against $M$;
\item $C$ is the reality-constrained classifier row comparing model-facing signatures with the reality-facing signature row $S$;
\item $F$ is the GAP-admissible compression row, recording the indexed sequence of approximation, finite Cauchy, Real-envelope, observer-budget, and residue stages accepted by the displayed classifier;
\item $L$ is the ledger row recording every hidden source, compressed stage, rejected signature omission, and open residue of the tower;
\item $H$ records componentwise $\hsame$ transport among source, observation-data, model, signature, classifier, compression, ledger, provenance, and local-name rows;
\item $R$ records the displayed $\Cont$ route from source observation to model readback, signature comparison, compression use, and ledger inspection;
\item $P$ is the $\Pkg$ provenance over \autoref{ch:concrete-instances-observationreflectionpacket-namecert}, \autoref{ch:concrete-instances-onticstate-namecert}, \autoref{ch:concrete-instances-approximation-namecert}, \autoref{ch:concrete-instances-finite-cauchy-approximation-namecert}, \autoref{ch:concrete-instances-realapproximationenvelope-namecert}, \autoref{ch:concrete-instances-observer-filter-budget-selector-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RealityConstrainedApproximationTowerUp}$ row.
\end{enumerate}
The classifier admits $T$ only when the physical signature, GAP-admissible compression, and ledger rows are all displayed on the same indexed tower. The carrier has no coordinate for mathematical approximation divorced from physical signature, compression without a listed GAP row, erased compression residue, quotient-real equality, selected host limits, host-level physical law, or ambient completeness.
\end{definition}

\begin{theorem}[Reality-constrained approximation-tower NameCert obligations]
\label{thm:reality-constrained-approximation-tower-namecert-obligations}
For every accepted \RealityConstrainedApproximationTowerUp carrier
$$
T=(O,D,M,S,C,F,L,H,R,P,N),
$$
the local $\NameCert_{\RealityConstrainedApproximationTowerUp}$ surface consists exactly of carrier admission for $T$, ontic source exposure through $O$, observation-data readback through $D$, model exposure through $M$, physical-signature display through $S$, reality-constrained classifier exactness through $C$, GAP-admissible compression through $F$, ledger coverage through $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ route replay through $R$, dependency provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier definition. The positive route exposes the source row $O$, observation-data row $D$, model row $M$, physical-signature row $S$, classifier $C$, GAP-admissible compression row $F$, and ledger row $L$ before the structural rows are read.

The structural rows are attached to that same route. Transport through $H$ is componentwise over the displayed rows, replay through $R$ follows the same tower ledger, provenance through $P$ names the listed siblings, and $N$ names no additional coordinate.

Thus the local NameCert surface is exhausted by the displayed rows. Since no additional coordinate exists for detached mathematical approximation, unledgered physical signature data, a hidden classifier, or an ambient completion principle, the obligations are exactly the ones listed.
\end{proof}
\leanchecked{BEDC.Derived.RealityConstrainedApproximationTowerUp.RealityConstrainedApproximationTowerTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Reality-constrained approximation-tower non-escape]
\label{thm:reality-constrained-approximation-tower-nonescape}
Every mathematical approximation consumed through an accepted \RealityConstrainedApproximationTowerUp packet factors through the displayed physical-signature row $S$, classifier row $C$, GAP-admissible compression row $F$, and tower ledger $L$. It cannot replace physical-fit signature data by using only the model row $M$, host equality, quotient-real equality, selected limits, or ambient completeness.
\end{theorem}
\begin{proof}
Start with the carrier $T=(O,D,M,S,C,F,L,H,R,P,N)$. Its only approximation-facing coordinates after model readback are the physical-signature row $S$, classifier row $C$, compression row $F$, and ledger row $L$.

Apply the obligation surface of \autoref{thm:reality-constrained-approximation-tower-namecert-obligations}. Any mathematical classifier whose stability depends on hidden source history, omitted physical signature, or compressed residue must be recorded through $S,C,F,L$ rather than silently transported across $M$.

It remains to exhaust the excluded routes. The model row $M$ records the visible mathematical representation, and the structural rows $H,R,P,N$ only transport, replay, package, and name displayed data. None of these rows contains host equality, quotient-real equality, selected limits, ambient completeness, or a second physical-fit channel. Thus mathematical approximation cannot replace the displayed physical-fit signature data.
\end{proof}
\leanchecked{BEDC.Derived.RealityConstrainedApproximationTowerUp.RealityConstrainedApproximationTowerNonescape}

\begin{theorem}[Reality-constrained approximation-tower sibling independence]
\label{thm:reality-constrained-approximation-tower-sibling-independence}
The \RealityConstrainedApproximationTowerUp carrier is not bijective to the observation-reflection-packet, ontic-state, finite-observation-interface, closed-observation-system, reflection-runtime-checkpoint, approximation, finite-Cauchy-approximation, Real-approximation-envelope, observer-filter-budget-selector, or residue surfaces named by its provenance. Each sibling lacks at least one of the joint ontic source, observation-data row, model row, physical-signature row, classifier row, GAP-admissible compression row, ledger row, transport, continuation, provenance, and local NameCert coordinates required by \autoref{def:reality-constrained-approximation-tower-packet}.
\end{theorem}
\leanchecked{BEDC.Derived.RealityConstrainedApproximationTowerUp.RealityConstrainedApproximationTower\_sibling\_independence\_boundary}
\begin{proof}
Inspect the observation-facing siblings. The observation-reflection packet supplies a readback route but not the full GAP-admissible compression ledger. The ontic-state packet names source state but not the classifier and tower ledger. The finite-observation-interface, closed-observation-system, and reflection-runtime-checkpoint surfaces each isolate an interface, closure, or runtime checkpoint without carrying the full physical-fit classifier across the tower.

Inspect the approximation-facing siblings. The approximation carrier supplies approximation rows but not the full physical-signature and ledger inventory. The finite Cauchy approximation carrier supplies finite precision windows but not the ontic source and physical-signature classifier. The Real approximation envelope supplies Real-facing boundary rows but not the selected observation bundle with omitted-row residue. The observer-filter budget selector supplies selected and omitted observer rows but not the full indexed tower from ontic source to model readback.

The residue surface is also separated. It records what remains outside a given admission, while the tower carrier binds residue to the same packet that contains source, observation data, model, physical signature, classifier, GAP-admissible compression, ledger, transport, continuation, provenance, and local naming rows.

Therefore no listed sibling carries all coordinates of $T$ and no coordinate of $T$ can be deleted without changing the accepted NameCert surface. A bijection preserving the local obligations would have to preserve all displayed rows, which none of the siblings can do.
\end{proof}

\falsifiablePrediction{An accepted $\RealityConstrainedApproximationTowerUp$ packet cannot identify two representations by a mathematical classifier unless their displayed physical signature rows agree through the same tower ledger.}

\independenceWitness{observationreflectionpacket, onticstate, finiteobservationinterface, closedobservationsystem, reflectionruntimecheckpoint, approximation, finite-cauchy-approximation, real-approximation-envelope, observer-filter-budget-selector, residue: no listed sibling is bijective to $\RealityConstrainedApproximationTowerUp$ because only this packet carries ontic source, observation data, model row, physical signature, classifier, GAP-admissible compression, tower ledger, hsame transport, Cont route, Pkg provenance, and local NameCert rows together. The tower ledger and physical-fit classifier separate these coordinates from every sibling surface.}

The packet composes observationreflectionpacket, onticstate, finiteobservationinterface, closedobservationsystem, reflectionruntimecheckpoint, approximation, finite-cauchy-approximation, real-approximation-envelope, observer-filter-budget-selector, and residue into the displayed approximation-tower surface.

Lean development for this route must provide $\mathsf{Nontrivial}\ \RealityConstrainedApproximationTowerUp$ and $\mathsf{FieldFaithful}\ \RealityConstrainedApproximationTowerUp$ instances in \texttt{lean4/BEDC/Derived/RealityConstrainedApproximationTowerUp/TasteGate.lean}.

\closureat{RealityConstrainedApproximationTowerUp}{scopedStr}[BEDC.Derived.RealityConstrainedApproximationTowerUp.RealityConstrainedApproximationTowerTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\RealityConstrainedApproximationTowerUp}
  \constructivestory{A $\RealityConstrainedApproximationTowerUp$ packet is generated from ontic source, observation-data, model, physical-signature, classifier, GAP-admissible compression, ledger, transport, continuation, provenance, and local NameCert rows.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:reality-constrained-approximation-tower-packet}, \autoref{thm:reality-constrained-approximation-tower-namecert-obligations}, \autoref{thm:reality-constrained-approximation-tower-nonescape}, \autoref{thm:reality-constrained-approximation-tower-sibling-independence}, and \leanchecked{BEDC.Derived.RealityConstrainedApproximationTowerUp.taste\_gate} bind the carrier, NameCert obligations, non-escape surface, sibling-independence boundary, and TasteGate instance for the finite tower.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RealityConstrainedApproximationTowerUp.RealityConstrainedApproximationTowerTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not claim bridge checking, public-object closure, mature closure, or axiom-clean verification for the full theory surface.}
  \upgradepath{The next paper-side obligation is public export of the same carrier, NameCert surface, non-escape boundary, sibling-independence witness, and TasteGate handoff.}
\end{closurestatus}
