\chapter{A Concrete Naming Certificate for $\IntervalLengthUp$}
\label{ch:concrete-instances-interval-length-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the
$\IntervalLengthUp$ packet names the finite diameter data of a closed
interval before any appeal to compactness, selected endpoints, or completed
real equality. It sits after the dyadic arithmetic surface of
\autoref{ch:concrete-instances-dyadicratcore-namecert}, the endpoint window
interfaces of \autoref{ch:concrete-instances-dyadicinterval-namecert} and
\autoref{ch:concrete-instances-rationalinterval-namecert}, and the
real-window enclosure route of
\autoref{ch:concrete-instances-real-interval-enclosure-namecert}. Downstream
uses in \autoref{ch:concrete-instances-real-namecert} read only this finite
diameter certificate when a $\RealUp$ or $\RegSeqRatUp$ argument needs the
length of an interval window.

\begin{definition}[IntervalLength carrier]
\label{def:interval-length-carrier}
An $\IntervalLengthUp$ carrier is a finite $\BHist$ packet
$$
I=(L,R,O,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the left endpoint row, accepted either as a
$\DyadicIntervalUp$ endpoint projection or as a $\RationalIntervalUp$
endpoint row.
\item $R$ is the right endpoint row, accepted through the same endpoint
surface as $L$.
\item $O$ is the endpoint-order ledger proving that the displayed left row
precedes the displayed right row in the corresponding finite rational or
dyadic comparison surface.
\item $D$ is the dyadic diameter row, a $\DyadicRatCoreUp$ row naming the
finite value read as $R-L$ on the common endpoint window.
\item $E$ is the real-interval enclosure handoff row, linking the same
endpoint and diameter data to the finite enclosure surface of
\autoref{ch:concrete-instances-real-interval-enclosure-namecert}.
\item $H$ records componentwise $\hsame$ transport for the endpoint rows,
order ledger, diameter row, enclosure handoff, continuation row, provenance
row, and local naming row.
\item $C$ records the $\Cont$ replay by which a later finite consumer reads
the same endpoint, order, diameter, and enclosure rows.
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$,
$\DyadicIntervalUp$, $\RationalIntervalUp$,
$\RealIntervalEnclosureUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\IntervalLengthUp}$ row.
\end{enumerate}
The carrier predicate is exactly the assertion that these nine rows form one
finite interval-length packet. It has no coordinate for open-cover
compactness, selected endpoints, quotient real equality, trichotomy, or
ambient completeness.
\end{definition}
\leanchecked{BEDC.Derived.IntervalLengthUp.IntervalLengthTasteGate\_single\_carrier\_alignment}

\begin{theorem}[IntervalLength NameCert obligations]
\label{thm:interval-length-namecert-obligations}
For every accepted $\IntervalLengthUp$ carrier
$I=(L,R,O,D,E,H,C,P,N)$, the local
$\NameCert_{\IntervalLengthUp}$ surface consists exactly of the following
finite obligation rows:
\begin{enumerate}
\item carrier admission for the two endpoint rows, endpoint-order ledger,
dyadic diameter row, enclosure handoff, componentwise transport,
continuation replay, package provenance, and local naming row;
\item endpoint-order exposure, requiring every length read to display the
same $O$ row that certifies the endpoint orientation;
\item diameter exactness, requiring $D$ to be the displayed
$\DyadicRatCoreUp$ subtraction row $R-L$ on the common endpoint window;
\item enclosure handoff, requiring $E$ to route the same endpoints and
diameter into the finite real-interval enclosure surface;
\item classifier transport, requiring $H$ to transport endpoint,
order, diameter, enclosure, provenance, and naming rows componentwise;
\item replay stability, requiring $C$ to replay the same finite rows for
later $\RegSeqRatUp$ and $\RealUp$ consumers;
\item provenance exhaustion, requiring $P$ to name every consumed
$\DyadicRatCoreUp$, $\DyadicIntervalUp$, $\RationalIntervalUp$, and
$\RealIntervalEnclosureUp$ source row;
\item ledger non-escape, excluding any read through open-cover compactness,
selected endpoint choice, quotient real equality, trichotomy, or ambient
completeness.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:interval-length-carrier}. The projection
exposes exactly two endpoint rows, one endpoint-order ledger, one dyadic
diameter row, one enclosure handoff, and the structural rows $H,C,P,N$.

Endpoint-order exposure is the row $O$. Since the carrier stores $D$ next to
$O$, a consumer cannot read a length without also reading the finite
orientation ledger for the same endpoint window.

Diameter exactness is the row $D$. It is typed as a $\DyadicRatCoreUp$
subtraction row on the displayed endpoint surface, so the value read by a
consumer is the finite dyadic difference $R-L$ and not a host metric length.

The handoff row $E$ is then read through the real-interval enclosure surface.
Transport by $H$ and replay by $C$ preserve the same endpoint, order,
diameter, and enclosure rows componentwise.

Finally, $P$ and $N$ exhaust provenance and naming. Because the carrier has
no coordinate for open-cover compactness, selected endpoints, quotient real
equality, trichotomy, or ambient completeness, the listed non-escape
conditions are immediate from the packet inventory.
\end{proof}

\begin{theorem}[IntervalLength dyadic diameter handoff]
\label{thm:interval-length-dyadic-diameter-handoff}
Every $\RealUp$ or $\RegSeqRatUp$ consumer of an accepted
$\IntervalLengthUp$ packet reads the interval diameter only through the
displayed route
$$
L,R,O \longmapsto D \longmapsto E \longmapsto H,C,P,N .
$$
The route factors through $\DyadicRatCoreUp$, $\DyadicIntervalUp$,
$\RationalIntervalUp$, $\RealIntervalEnclosureUp$, $\BHist$, $\hsame$,
$\Cont$, $\Pkg$, and $\NameCert$ rows. It does not expose an ambient metric
length, a selected endpoint pair, quotient equality of real names, trichotomy,
open-cover compactness, or a completeness witness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $I=(L,R,O,D,E,H,C,P,N)$. The only endpoint
coordinates are $L$ and $R$, and the only orientation coordinate attached to
them is $O$.

The diameter coordinate is $D$. By
\autoref{def:interval-length-carrier}, $D$ is a displayed
$\DyadicRatCoreUp$ row computed from the same endpoint window, so every
diameter read first factors through the finite dyadic arithmetic surface.

The enclosure handoff is $E$. It routes the same endpoint and diameter rows
into the finite real-interval enclosure packet, which is the only surface
available to a $\RealUp$ consumer at this boundary.

Finally $H,C,P,N$ package transport, replay, provenance, and local naming.
Thus a $\RealUp$ or $\RegSeqRatUp$ consumer receives exactly the displayed
BEDC rows and no ambient metric length, selected endpoint pair, quotient
real equality, trichotomy, compactness theorem, or completeness datum.
\end{proof}

\closureat{IntervalLengthUp}{seedStr}

\begin{closurestatus}{\IntervalLengthUp}
  \constructivestory{An $\IntervalLengthUp$ packet is generated from displayed left and right endpoint rows, an endpoint-order ledger, a dyadic diameter row, a real-interval enclosure handoff, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:interval-length-carrier}, \autoref{thm:interval-length-namecert-obligations}, and \autoref{thm:interval-length-dyadic-diameter-handoff} seed the finite interval-diameter surface used by DyadicRatCore, DyadicInterval, RationalInterval, RealIntervalEnclosure, RegSeqRat, and Real consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected endpoints, quotient real equality, trichotomy, ambient completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint-order exposure, diameter exactness, enclosure handoff, classifier transport, replay stability, provenance exhaustion, and ledger non-escape proofs for BEDC.Derived.IntervalLengthUp.}
\end{closurestatus}
