\chapter{A Concrete Naming Certificate for $\LocatedRegularizationUp$}
\label{ch:concrete-instances-located-regularization-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\LocatedRegularizationUp$ packet records the finite boundary where a Cauchy stream is regularized while retaining positive locatedness and apartness evidence. It sits after the regularization route of \autoref{ch:concrete-instances-cauchyregularization-namecert}, the positive apartness boundary of \autoref{ch:concrete-instances-cauchy-real-apartness-namecert}, the Real-facing Cauchy readiness surface of \autoref{ch:concrete-instances-real-cauchy-criterion-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives later Real and completion chapters one finite route from source Cauchy data to located regular names; it is not a quotient stream, not a selected limit, not a trichotomy decision, not countable choice, not ambient $\RealUp$ completeness, and not bridge checking.

\begin{definition}[LocatedRegularization carrier]
\label{def:located-regularization-carrier}
A $\LocatedRegularizationUp$ carrier is a finite $\BHist$ packet
$$
L=(S,M,A,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source Cauchy stream row before regularization or locatedness evidence is read.
\item $M$ is the modulus-threshold row consumed from the $\CauchyRegularizationUp$ route.
\item $A$ is the positive located/apartness row consumed from the $\CauchyRealApartnessUp$ boundary.
\item $W$ is the finite $\StreamNameUp$ window schedule through which the source stream and apartness row are inspected.
\item $R$ is the $\RegSeqRatUp$ handoff obtained from the scheduled windows and the modulus threshold.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the dyadic radii, slack rows, and comparison tolerances used by the located window.
\item $E$ is the terminal $\RealUp$ seal for the regularized name after $W,R,D$ and the positive row $A$ have been displayed.
\item $H$ records componentwise $\hsame$ transports for $S,M,A,W,R,D,E$ and for the structural replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each located regularization request through $S,M,A,W,R,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedRegularizationUp$, $\CauchyRegularizationUp$, $\CauchyRealApartnessUp$, $\RealCauchyCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedRegularizationUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite located regularization surface. It contains no quotient stream, selected limit, trichotomy decision, countable-choice selector, ambient $\RealUp$ completeness witness, or bridge credential.
\end{definition}
\leanchecked{BEDC.Derived.LocatedRegularizationUp.LocatedRegularizationTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LocatedRegularization NameCert obligations]
\label{thm:located-regularization-namecert-obligations}
For every accepted $\LocatedRegularizationUp$ carrier $L=(S,M,A,W,R,D,E,H,C,P,N)$, the local $\NameCert_{\LocatedRegularizationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source Cauchy stream, modulus threshold, positive located/apartness row, finite windows, regular rational handoff, dyadic tolerance ledger, Real seal, transports, replay, provenance, and local naming rows;
\item located-window compatibility, requiring each positive locatedness read to inspect $S$ only through the $\StreamNameUp$ schedule $W$ and the dyadic ledger $D$ before $R$ or $E$ can be consumed;
\item apartness preservation, requiring the positive row $A$ to remain attached to the same scheduled regularization route $S,M,W,R,D$ under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item Real-seal nonescape, requiring every $\RealUp$-facing read of $E$ to pass through the displayed regularization, window, readback, tolerance, and positive-apartness rows rather than through a detached completed real;
\item provenance exhaustion, requiring every downstream Real, completion, Cauchy-criterion, or apartness consumer to read only $S,M,A,W,R,D,E,H,C,P,N$ and no quotient stream, selected limit, trichotomy, countable-choice source, ambient $\RealUp$ completeness principle, or bridge credential.
\end{enumerate}
No located-regularization obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-regularization-carrier}. The accepted packet lists the source stream, modulus threshold, positive located/apartness row, finite window schedule, regular rational handoff, dyadic tolerance ledger, Real seal, and structural rows.

For located-window compatibility, read the row order in the carrier. The positive row $A$ is not exported directly to a Real-facing consumer; it is inspected through the same finite window schedule $W$ and the same dyadic ledger $D$ that feed the regular rational handoff $R$.

Apartness preservation follows by row-order induction along the transported packet. The base step preserves $S,M,A$ by the corresponding coordinates of $H$, and the window, handoff, tolerance, and seal steps replay those transported rows through $C$ without changing the positive apartness source.

Real-seal nonescape is the terminal-row clause. The seal $E$ appears only after $W,R,D$ and $A$ have been displayed, so a consumer cannot obtain a detached completed real, selected limit, quotient representative, or ambient completeness witness by projecting $E$.

Finally, provenance exhaustion is projection from $P$ and $N$ together with the absence of further carrier coordinates. Since $L$ has only the rows $S,M,A,W,R,D,E,H,C,P,N$, downstream Cauchy-criterion, apartness, Real, and completion consumers receive exactly that finite route and no excluded bridge or choice data.
\end{proof}

\begin{theorem}[LocatedRegularization real-seal factorization]
\label{thm:located-regularization-real-seal-factorization}
For every accepted $\LocatedRegularizationUp$ carrier $L=(S,M,A,W,R,D,E,H,C,P,N)$, every $\RealUp$-facing read of the terminal seal $E$ factors through the displayed finite row sequence
$$
S \longrightarrow M \longrightarrow A \longrightarrow W \longrightarrow R \longrightarrow D \longrightarrow E
$$
together with the componentwise transport, replay, provenance, and local naming rows $H,C,P,N$. Thus the seal can be consumed only after the source Cauchy stream $S$, the $\CauchyRegularizationUp$ modulus threshold $M$, the $\CauchyRealApartnessUp$ positive row $A$, the $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ handoff $R$, and the $\DyadicRatCoreUp$ ledger $D$ have all been displayed on the same carrier route. The factorization provides no quotient stream, selected limit, trichotomy decision, countable-choice selector, ambient $\RealUp$ completeness witness, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted carrier to the row list of \autoref{def:located-regularization-carrier}. The seal coordinate $E$ is not a standalone Real object in that list; it is the terminal row following the source stream, regularization threshold, positive apartness row, finite windows, regular rational handoff, and dyadic tolerance ledger.

Next inspect the local obligation surface of \autoref{thm:located-regularization-namecert-obligations}. Located-window compatibility forces the positive row $A$ to be read through $W$ and $D$, apartness preservation keeps $A$ attached to the route $S,M,W,R,D$ under $H$ and $C$, and the Real-seal nonescape row requires every $\RealUp$ consumer of $E$ to use that same displayed route.

It remains only to exclude alternate exits. The carrier has no coordinates for quotient streams, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, or bridge credentials, and provenance exhaustion says that downstream Real and completion consumers may read only $S,M,A,W,R,D,E,H,C,P,N$. Therefore every accepted seal read factors through the stated finite rows before reaching $E$.
\end{proof}

\closureat{LocatedRegularizationUp}{seedStr}

\begin{closurestatus}{\LocatedRegularizationUp}
  \constructivestory{A $\LocatedRegularizationUp$ packet is generated from a source Cauchy stream, a CauchyRegularization modulus threshold, a CauchyRealApartness positive row, StreamName finite windows, RegSeqRat handoff, DyadicRatCore tolerance rows, a terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-regularization-carrier}, \autoref{thm:located-regularization-namecert-obligations}, and \autoref{thm:located-regularization-real-seal-factorization} seed the finite located regularization boundary between Cauchy regularization, positive apartness, Real Cauchy readiness, and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-window compatibility, apartness preservation, provenance exhaustion, and a Lean carrier/obligation formalization for BEDC.Derived.LocatedRegularizationUp.}
\end{closurestatus}
