\chapter{A Concrete Naming Certificate for $\RiemannIntegrableUp$}
\label{ch:concrete-instances-riemann-integrable-namecert}
\origin{human}

Following Riemann and Bishop--Bridges constructive analysis, the $\RiemannIntegrableUp$ packet names finite Darboux-gap evidence that an integrand admits integration data without already choosing an integral value. It sits over the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the dyadic partition ledger of \autoref{ch:concrete-instances-dyadic-partition-namecert}, the Darboux finite-sum boundary of \autoref{ch:concrete-instances-darboux-sum-namecert}, the tagged-mesh integration route of \autoref{ch:concrete-instances-riemannintegral-namecert}, and the regulated approximation handoff of \autoref{ch:concrete-instances-regulated-function-namecert}. The packet gives downstream integration chapters a displayed finite gap interface without importing a selected integral value, host function quotients, measure-theoretic integration, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Riemann integrable carrier]
\label{def:riemann-integrable-carrier}
A $\RiemannIntegrableUp$ carrier is a finite $\BHist$ packet
$$
J=(D,M,L,U,G,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the real-domain row, read through the terminal $\RealUp$ seal and the interval-facing data carried by \autoref{ch:concrete-instances-real-namecert}.
\item $M$ is the $\DyadicPartitionUp$ ledger naming the finite ordered dyadic partition on which the Darboux comparison is witnessed.
\item $L$ and $U$ are the lower and upper Darboux-sum rows, read through the $\DarbouxSumUp$ boundary of \autoref{ch:concrete-instances-darboux-sum-namecert} over the partition row $M$.
\item $G$ is the finite Darboux-gap ledger, displaying a dyadic tolerance request together with the comparison that the upper row $U$ and lower row $L$ meet that request.
\item $T$ is the tagged-mesh and regulated-function handoff row, exposing only the $\RiemannIntegralUp$ and $\RegulatedFunctionUp$ consumers that may later use the displayed gap evidence.
\item $H$ records componentwise $\hsame$ transport for the real-domain row, partition row, lower and upper Darboux rows, gap ledger, handoff row, continuation replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay from the real-domain row to the partition row, from the partition row to the lower and upper Darboux rows, from those rows to the gap ledger, and from the gap ledger to the downstream handoff row.
\item $P$ is the $\Pkg$ provenance over $\RiemannIntegrableUp$, $\RealUp$, $\DyadicPartitionUp$, $\DarbouxSumUp$, $\RiemannIntegralUp$, $\RegulatedFunctionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RiemannIntegrableUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,M,L,U,G,T,H,C,P,N$. It has no coordinate for a selected integral value, quotient equality of host functions, measure-theoretic integration, open-cover compactness, a choice-selected partition family, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.RiemannIntegrableUp.RiemannIntegrableTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Riemann integrable NameCert obligations]
\label{thm:riemann-integrable-namecert-obligations}
For every accepted $\RiemannIntegrableUp$ carrier
$$
J=(D,M,L,U,G,T,H,C,P,N),
$$
the local $\NameCert_{\RiemannIntegrableUp}$ surface consists exactly of carrier admission, real-domain admission, dyadic partition admission, lower and upper Darboux-sum compatibility, finite gap routing, tagged-mesh and regulated-function handoff, componentwise transport, continuation replay, provenance, local naming, and non-escape from selected integral values, host function quotients, measure-theoretic integration, open-cover compactness, choice-selected partition families, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is the projection of \autoref{def:riemann-integrable-carrier}. The accepted packet displays only the real-domain row $D$, partition ledger $M$, lower and upper Darboux rows $L,U$, gap ledger $G$, downstream handoff $T$, transports $H$, continuations $C$, provenance $P$, and local name $N$.

The analytic rows are finite. The real-domain row is read through $\RealUp$, the partition row is read through $\DyadicPartitionUp$, and the two Darboux rows are read through the $\DarbouxSumUp$ surface over the same displayed partition.

The gap obligation is then the row $G$. It records that the displayed upper and lower rows answer the carried dyadic tolerance request before any tagged-mesh or regulated-function consumer may inspect $T$.

Transport and replay preserve the same route componentwise. Since the carrier has no coordinate for an integral value, a host quotient, a measure object, open-cover compactness, a choice-selected partition family, or ambient completeness, the listed rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Riemann integrable Darboux-gap route]
\label{thm:riemann-integrable-darboux-gap-route}
Every accepted $\RiemannIntegrableUp$ packet exposes integration-facing evidence only through the finite route
$$
D\longmapsto M\longmapsto (L,U)\longmapsto G\longmapsto T .
$$
The handoff row $T$ may be consumed by $\RiemannIntegralUp$ or $\RegulatedFunctionUp$ chapters only after the real-domain row, dyadic partition ledger, lower and upper Darboux rows, and finite Darboux-gap ledger have all been displayed.
\end{theorem}
\begin{proof}
Start with an integration-facing consumer request. The continuation row $C$ first replays the real-domain row $D$ and then the finite partition row $M$, so the request is already confined to displayed real and dyadic partition data.

The rows $L$ and $U$ are read next through the $\DarbouxSumUp$ boundary. They use the same partition row $M$, hence the upper-minus-lower comparison is a finite Darboux comparison over displayed cells.

Only after these rows are present can the gap ledger $G$ be read. The row $G$ supplies the finite tolerance evidence that downstream consumers need, and the handoff row $T$ records the permitted $\RiemannIntegralUp$ and $\RegulatedFunctionUp$ uses of that evidence.

Thus the packet exports integrability evidence without exporting an already chosen integral value. The excluded host objects are absent from the carrier, so no consumer can recover them from the Darboux-gap route.
\end{proof}

\closureat{RiemannIntegrableUp}{seedStr}

\begin{closurestatus}{\RiemannIntegrableUp}
  \constructivestory{A $\RiemannIntegrableUp$ packet is generated from a real-domain row, a finite dyadic partition ledger, lower and upper Darboux-sum rows, a finite Darboux-gap ledger, a tagged-mesh and regulated-function handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riemann-integrable-carrier}, \autoref{thm:riemann-integrable-namecert-obligations}, and \autoref{thm:riemann-integrable-darboux-gap-route} seed the finite Darboux-gap integrability interface over $\RealUp$, $\DyadicPartitionUp$, $\DarbouxSumUp$, $\RiemannIntegralUp$, $\RegulatedFunctionUp$, and $\BHist$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected integral values, host function quotients, measure-theoretic integration, open-cover compactness, choice-selected partition families, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, real-domain admission, dyadic partition admission, Darboux-sum compatibility, finite gap routing, downstream handoff, non-escape, and field faithfulness for BEDC.Derived.RiemannIntegrableUp.}
\end{closurestatus}
