\chapter{A Concrete Naming Certificate for $\CauchyCompressionUp$}
\label{ch:concrete-instances-cauchy-compression-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CauchyCompressionUp$ packet records the finite constructive operation that turns modulus-controlled Cauchy data into a fast Cauchy certificate. It sits over the visible modulus schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the compressed fast-Cauchy interface of \autoref{ch:concrete-instances-fastcauchy-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies the L10 Real and Completion route with a standard finite bridge from an explicit modulus to a fast Cauchy certificate; it is not quotient stream equality, a selected limit, countable choice, host equality, ambient completeness, Lean verification, or a standard bridge.

\begin{definition}[Cauchy compression carrier]
\label{def:cauchy-compression-carrier}
A $\CauchyCompressionUp$ carrier is a finite $\BHist$ packet
$$
C=(M,S,D,Q,F,E,H,C_0,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\CauchyModulusUp$ schedule row, recording the visible request-to-threshold map used to choose the finite tail windows.
\item $S$ is the $\StreamNameUp$ window row, listing exactly the finite stream observations selected by the modulus schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, storing the requested radii, slack comparisons, and dyadic arithmetic consumed by the selected windows.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the same selected windows and tolerance ledger.
\item $F$ is the $\FastCauchyUp$ compressed output row, recording the fast Cauchy certificate produced from $M,S,D,Q$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the modulus, window, tolerance, readback, and fast-Cauchy rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the modulus schedule, selected windows, tolerance ledger, regular readback, fast output, real seal, replay, provenance, and local naming rows.
\item $C_0$ records displayed $\Cont$ replay from each precision request through $M,S,D,Q,F,E$ and then through $H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompressionUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\FastCauchyUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompressionUp}$ row.
\end{enumerate}
The classifier compares accepted compression packets only through the displayed rows $M,S,D,Q,F,E,H,C_0,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, host equality, ambient $\RealUp$ completeness, Lean evidence, or standard-bridge data.
\end{definition}

\begin{theorem}[Cauchy compression NameCert obligations]
\label{thm:cauchy-compression-namecert-obligations}
For every accepted $\CauchyCompressionUp$ carrier
$$
C=(M,S,D,Q,F,E,H,C_0,P,N),
$$
the local $\NameCert_{\CauchyCompressionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the $\CauchyModulusUp$ schedule $M$, $\StreamNameUp$ windows $S$, $\DyadicRatCoreUp$ tolerance ledger $D$, $\RegSeqRatUp$ readback $Q$, $\FastCauchyUp$ compressed output $F$, $\RealUp$ seal $E$, and structural rows $H,C_0,P,N$;
\item modulus admission, requiring each precision request to enter through the displayed schedule $M$ before any stream window is inspected;
\item finite window selection, requiring $S$ to contain exactly the windows selected by $M$ for the displayed precision requests;
\item dyadic accounting, requiring $D$ to store exactly the tolerance radii and slack comparisons consumed by the selected windows;
\item readback and fast-output routing, requiring $Q$ and $F$ to remain downstream of $M,S,D$ and to use no unlisted stream coordinate;
\item real-seal routing, requiring $E$ to be reached only after the compressed fast-Cauchy output has been displayed;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C_0,P,N$;
\item non-escape for quotient streams, selected limits, countable choice, host equality, ambient completeness, Lean verification, and standard-bridge data.
\end{enumerate}
No Cauchy compression obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-compression-carrier}. The analytic rows are the visible modulus schedule, selected stream windows, dyadic tolerance ledger, regular readback, fast-Cauchy output, and terminal real seal; the remaining rows transport, replay, source, and name that same route.

The modulus row is read before any window is opened. For each displayed precision request, $M$ supplies a finite threshold, and the window row $S$ records only the observations selected from that threshold. The construction therefore uses visible finite windows rather than a quotient stream or a selected limiting object.

The selected windows then pass through the dyadic ledger and readback rows. The ledger $D$ contains the requested radii and slack comparisons, while $Q$ is the regular rational readback obtained from those same displayed windows.

The compressed row $F$ is downstream of $M,S,D,Q$. It is the only $\FastCauchyUp$ coordinate in the carrier, so every accepted fast certificate is produced from the displayed modulus-controlled route.

Finally $E,H,C_0,P,N$ seal, transport, replay, source, and name the same finite route. Since none of the excluded objects appears as a carrier coordinate, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Cauchy compression regular-sequence handoff]
\label{thm:cauchy-compression-regseqrat-handoff}
Let
$$
C=(M,S,D,Q,F,E,H,C_0,P,N)
$$
be an accepted $\CauchyCompressionUp$ carrier. Every precision request answered by the fast Cauchy row $F$ has the same finite route through the regular rational row $Q$ and the real seal $E$:
$$
M\longmapsto S\longmapsto D\longmapsto Q\longmapsto F\longmapsto E\longmapsto H,C_0,P,N .
$$
Consequently a $\RegSeqRatUp$ or $\RealUp$ consumer receives the displayed modulus schedule, selected windows, tolerance ledger, regular readback, fast-Cauchy certificate, seal, transport, replay, provenance, and local naming. The handoff does not export quotient streams, selected limits, countable choice, host equality, ambient completeness, Lean evidence, or standard-bridge data.
\end{theorem}
\begin{proof}
Begin with the displayed precision request and read the modulus schedule $M$. The schedule selects a finite threshold, and the window row $S$ records the stream observations opened at that threshold.

Pass the selected windows through $D$ and $Q$. The dyadic ledger supplies the tolerance arithmetic, and the regular rational readback records the observation that the downstream consumer can inspect.

Now read the compressed row $F$. Because $F$ is downstream of $M,S,D,Q$, the fast Cauchy certificate is obtained from the same finite route that produced the regular rational readback.

The terminal seal $E$ is reached after $F$, and the structural rows $H,C_0,P,N$ preserve the displayed route componentwise. Thus the $\RegSeqRatUp$ handoff and the $\RealUp$ handoff consume the same finite data and introduce none of the excluded quotient, selector, choice, equality, completeness, verification, or bridge objects.
\end{proof}

\falsifiablePrediction{Every $\CauchyCompressionUp$ precision read factors through a CauchyModulus schedule, selected StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a FastCauchy compressed output, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchymodulus, fastcauchy, streamname, dyadicratcore, regseqrat, real: $\CauchyCompressionUp$ is not bijective to any listed sibling because it jointly carries visible modulus scheduling, finite window selection, dyadic tolerance accounting, regular rational readback, fast Cauchy compression, terminal real sealing, transport, replay, provenance, and local naming.}

\closureat{CauchyCompressionUp}{seedStr}

\begin{closurestatus}{\CauchyCompressionUp}
  \constructivestory{A $\CauchyCompressionUp$ packet is generated from a CauchyModulus schedule, selected StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a FastCauchy compressed output, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-compression-carrier}, \autoref{thm:cauchy-compression-namecert-obligations}, and \autoref{thm:cauchy-compression-regseqrat-handoff} seed the finite route from visible modulus-controlled Cauchy data to a fast Cauchy certificate consumed by regular rational and Real interfaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, host equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, modulus admission, finite window selection, dyadic accounting, readback and fast-output routing, real-seal routing, and regular-sequence handoff for BEDC.Derived.CauchyCompressionUp.}
\end{closurestatus}
