\chapter{A Concrete Naming Certificate for $\CauchyCompletionComparisonUp$}
\label{ch:concrete-instances-cauchy-completion-comparison-namecert}
\origin{human}

Following Bishop and Bridges, Kelley, and Bourbaki, the $\CauchyCompletionComparisonUp$ packet records the finite BEDC surface by which a unit-and-universal-property completion presentation is compared with a functorial metric-completion presentation. It reads the dense unit route of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the universal-property route of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the functorial action route of \autoref{ch:concrete-instances-cauchy-completion-functoriality-namecert}, the metric-completion boundary of \autoref{ch:concrete-instances-metriccompletionfinite-namecert}, the finite stream window of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names a comparison certificate for displayed completion presentations only; it does not identify quotient completions, choose representatives, assert host equality, or import completeness of $\RealUp$.

\begin{definition}[CauchyCompletionComparison carrier]
\label{def:cauchy-completion-comparison-carrier}
A $\CauchyCompletionComparisonUp$ carrier is a finite $\BHist$ packet
$$
K=(U,V,F,M,R,S,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\CauchyCompletionUnitUp$ source-admission row for the unit-and-universal-property presentation.
\item $V$ is the $\CompletionUniversalPropertyUp$ row recording the finite extension obligation and its displayed uniqueness comparison.
\item $F$ is the $\CauchyCompletionFunctorialityUp$ row recording the corresponding completed-map route on the functorial side.
\item $M$ is the $\MetricCompletionUp$ row recording the metric-completion presentation whose finite Cauchy data are being compared with $U,V,F$.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row shared by the two presentations.
\item $S$ is the finite $\StreamNameUp$ window family inspected before either presentation reaches a completion-facing seal.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and diameter ledger attached to the same stream windows.
\item $E$ is the terminal $\RealUp$ seal row reached only after the shared $S,D,R$ route has been displayed.
\item $H$ records componentwise $\hsame$ transport for $U,V,F,M,R,S,D,E$ and the structural rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
U,V,F,M\longmapsto S,D,R\longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionComparisonUp$, $\CauchyCompletionUnitUp$, $\CompletionUniversalPropertyUp$, $\CauchyCompletionFunctorialityUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionComparisonUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, countable choice, host equality of completed objects, open-cover compactness, or completeness of $\RealUp$.
\end{definition}
\leanchecked{BEDC.Derived.CauchyCompletionComparisonUp.CauchyCompletionComparisonTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyCompletionComparison NameCert obligations]
\label{thm:cauchy-completion-comparison-namecert-obligations}
For every accepted $\CauchyCompletionComparisonUp$ carrier
$$
K=(U,V,F,M,R,S,D,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionComparisonUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the unit row, universal-property row, functorial row, metric-completion row, regular readback, stream windows, dyadic ledger, terminal seal, transport, replay, provenance, and local naming row;
\item shared-window coverage, requiring both presentations to inspect only the finite $\StreamNameUp$ windows in $S$ before reading $D,R,E$;
\item universal-to-functorial comparison, requiring any unit/universal-property completion consumer to pass through $U,V$ before it is compared with the functorial row $F$;
\item metric presentation comparison, requiring any metric-completion consumer to pass through $M$ and then the same $S,D,R,E$ route;
\item classifier stability, requiring transported packets with componentwise matching rows to replay the same comparison through $H$ and $C$;
\item non-escape, requiring $P,N$ to source and name no quotient completion equality, selected representative, countable-choice schedule, host equality, open-cover compactness, or completeness theorem for $\RealUp$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-comparison-carrier}. The accepted tuple displays exactly the four presentation rows $U,V,F,M$, the shared observation route $S,D,R,E$, and the structural rows $H,C,P,N$.

Shared-window coverage is proved by induction on the finite $\StreamNameUp$ windows in $S$. The empty window exposes no rational readback. In the cons step, the next displayed window contributes only its attached $\DyadicRatCoreUp$ tolerance row and $\RegSeqRatUp$ readback before the induction hypothesis replays the remaining windows.

The universal-to-functorial comparison is componentwise. The unit route $U$ supplies the dense source admission, $V$ supplies the extension and uniqueness surface, and $F$ supplies the functorial completed-map route over the same displayed source data.

The metric presentation comparison uses the same induction on $S$ and the same replay through $D,R,E$. Since $M$ has no separate terminal seal coordinate in the carrier, a metric-completion read reaches the public comparison only through the shared finite route.

Finally transport and naming are read from $H,C,P,N$. These rows preserve the displayed coordinates and add no quotient, representative-choice, countable-choice, host-equality, compactness, or real-completeness coordinate, so the listed rows exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.CauchyCompletionComparisonUp.CauchyCompletionComparisonCarrier\_namecert\_obligations}

\begin{theorem}[CauchyCompletionComparison route]
\label{thm:cauchy-completion-comparison-route}
Let
$$
K=(U,V,F,M,R,S,D,E,H,C,P,N)
$$
be an accepted $\CauchyCompletionComparisonUp$ carrier. Every consumer comparing the unit/universal-property presentation with the functorial metric-completion presentation factors through the finite route
$$
U,V,F,M\longmapsto S,D,R\longmapsto E\longmapsto H,C,P,N .
$$
The route is a comparison of displayed NameCert rows. It is not quotient completion equality, not selected representatives, not countable choice, not host equality of completed objects, not open-cover compactness, and not completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Begin with a comparison consumer and project the carrier. The only unit/universal-property coordinates are $U$ and $V$, and the only functorial coordinate is $F$.

The metric side is then forced through $M$. Any metric-completion read that reaches the comparison must expose the finite presentation row before the shared observation route is available.

We now replay the shared observation route by induction on $S$. At the base window there is no rational observation to compare. At each finite step, the displayed $\DyadicRatCoreUp$ tolerance in $D$ and the $\RegSeqRatUp$ readback in $R$ are transported componentwise, and the remaining windows are handled by the induction hypothesis.

The terminal seal is $E$. After $E$ is reached, $H$ and $C$ preserve the route under displayed $\hsame$ transport and $\Cont$ replay, while $P$ and $N$ record provenance and local naming. No other carrier coordinate exists, so the route cannot export any excluded completion or choice principle.
\end{proof}

\begin{theorem}[CauchyCompletionComparison sibling handoff]
\label{thm:cauchy-completion-comparison-sibling-handoff}
For an accepted $\CauchyCompletionComparisonUp$ carrier $K=(U,V,F,M,R,S,D,E,H,C,P,N)$, every sibling consumer from $\CauchyCompletionUnitUp$, $\CompletionUniversalPropertyUp$, $\CauchyCompletionFunctorialityUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ receives exactly the rows named in \autoref{def:cauchy-completion-comparison-carrier}. The handoff therefore preserves the shared finite comparison route and exports no quotient completion equality, selected representative, countable-choice schedule, host equality, open-cover compactness, or $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier and split the sibling consumers by their entry row.

Consumers entering through $\CauchyCompletionUnitUp$ or $\CompletionUniversalPropertyUp$ read $U,V$ first. They may continue to the functorial route $F$ and the metric route $M$, but only through the displayed comparison coordinates.

Consumers entering through $\CauchyCompletionFunctorialityUp$ or $\MetricCompletionUp$ read $F,M$ first. They still must pass through the same stream, dyadic, rational, and real-seal route $S,D,R,E$ before receiving a completion-facing comparison.

Consumers entering through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ are already inside the shared observation route. Induction on the finite window family $S$ shows that such consumers can inspect only the displayed window, tolerance, readback, and seal rows, preserved componentwise by $H$ and replayed by $C$.

The package row $P$ and local naming row $N$ source exactly these handoffs. Since the carrier has no coordinate for quotient equality, representative selection, countable choice, host equality, open-cover compactness, or real completeness, no sibling handoff can export one.
\end{proof}

\begin{theorem}[CauchyCompletionComparison seal agreement]
\label{thm:cauchy-completion-comparison-seal-agreement}
For an accepted $\CauchyCompletionComparisonUp$ carrier $K=(U,V,F,M,R,S,D,E,H,C,P,N)$, every comparison consumer that enters through the unit/universal-property route $U,V$ and every comparison consumer that enters through the functorial metric-completion route $F,M$ reaches the same displayed seal route
$$
S,D,R \longmapsto E .
$$
Equivalently, the public comparison surface has one $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ route after the presentation rows have been displayed. No second terminal seal, detached real route, quotient completion equality, selected representative, host equality, countable-choice schedule, open-cover compactness argument, or ambient $\RealUp$ completeness theorem is available to either consumer.
\end{theorem}
\begin{proof}
Project the accepted carrier using \autoref{def:cauchy-completion-comparison-carrier}. The presentation rows are exactly $U,V,F,M$, and the only analytic readback rows are $S,D,R,E$.

Apply the obligation surface of \autoref{thm:cauchy-completion-comparison-namecert-obligations}. The unit/universal-property consumer must expose $U,V$ before reaching the shared-window row, while the functorial metric-completion consumer must expose $F,M$ before reaching the same shared-window row.

Now apply the route theorem and sibling handoff, \autoref{thm:cauchy-completion-comparison-route} and \autoref{thm:cauchy-completion-comparison-sibling-handoff}. Both entry routes are replayed through $S,D,R$ and terminate at $E$, with $H,C,P,N$ preserving and naming only that displayed route. Since the carrier stores no second seal or excluded completion principle, the seal route is common to both consumers.
\end{proof}

\begin{theorem}[CauchyCompletionComparison nonquotient boundary]
\label{thm:cauchy-completion-comparison-nonquotient-boundary}
Let $K=(U,V,F,M,R,S,D,E,H,C,P,N)$ be an accepted $\CauchyCompletionComparisonUp$ carrier. Replacing the route
$$
U,V,F,M \longmapsto S,D,R \longmapsto E
$$
by quotient completion equality, selected representatives, host equality of completed objects, countable choice, open-cover compactness, or ambient $\RealUp$ completeness is outside the carrier and outside every $\NameCert_{\CauchyCompletionComparisonUp}$ handoff generated by $K$.
\end{theorem}
\begin{proof}
The carrier definition lists the full packet, so every admitted row is one of $U,V,F,M,R,S,D,E,H,C,P,N$. None of these rows is a quotient equality, a representative selector, a host-equality witness, a choice schedule, a compactness proof, or an ambient completeness theorem.

The NameCert obligations of \autoref{thm:cauchy-completion-comparison-namecert-obligations} require comparison consumers to expose the presentation rows and then the shared $S,D,R,E$ route. The route theorem fixes this order, and the sibling handoff theorem shows that every sibling consumer receives only the rows already named by the carrier.

Thus any attempted replacement by one of the excluded principles would need a coordinate not present in the packet or in its local $\NameCert$ surface. Such a replacement is therefore not a comparison handoff of $K$.
\end{proof}

\begin{closurestatus}{\CauchyCompletionComparisonUp}
  \constructivestory{A $\CauchyCompletionComparisonUp$ packet is generated from CauchyCompletionUnit, CompletionUniversalProperty, CauchyCompletionFunctoriality, and MetricCompletion presentation rows, shared finite StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a terminal Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-comparison-carrier}, \autoref{thm:cauchy-completion-comparison-namecert-obligations}, \autoref{thm:cauchy-completion-comparison-route}, \autoref{thm:cauchy-completion-comparison-sibling-handoff}, \autoref{thm:cauchy-completion-comparison-seal-agreement}, and \autoref{thm:cauchy-completion-comparison-nonquotient-boundary} seed the finite comparison surface between unit/universal-property and functorial metric-completion presentations.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host equality, open-cover compactness, completeness of $\RealUp$, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, shared-window coverage, presentation comparison, classifier stability, sibling handoff, and a Lean carrier/obligation formalization for BEDC.Derived.CauchyCompletionComparisonUp.}
\end{closurestatus}
