\chapter{A Concrete Naming Certificate for $\GrzegorczykRealUp$}
\label{ch:concrete-instances-grzegorczyk-real-namecert}
\origin{human}

Following Grzegorczyk's computable-real presentation and Weihrauch-style represented-space terminology, the $\GrzegorczykRealUp$ packet records the effective real-name boundary where a displayed algorithmic approximant is read through finite windows before it reaches the terminal real seal. It sits over the finite observation interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the computable-real service boundary of \autoref{ch:concrete-instances-computablereal-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the noncomputable contrast supplied by \autoref{ch:concrete-instances-speckersequence-namecert}. The packet names an effective route from approximant data to a $\RealUp$ consumer; it is not quotient stream equality, a completed real selected by choice, a host-real comparison, ambient $\RealUp$ completeness, or bridge checking.

\begin{definition}[Grzegorczyk real carrier]
\label{def:grzegorczyk-real-carrier}
A $\GrzegorczykRealUp$ carrier is a finite $\BHist$ packet
$$
G=(A,S,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the effective approximant row, recording the finite program, request precision, and rational output cell presented in Grzegorczyk's computable-real format.
\item $S$ is the finite $\StreamNameUp$ window row through which the approximant is inspected at the requested precisions.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording dyadic radii, slack comparisons, and finite error budgets attached to the approximant windows.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the scheduled windows and dyadic tolerance ledger.
\item $E$ is the terminal $\RealUp$ seal reachable only after the effective approximant, finite windows, dyadic ledger, and regular rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for $A,S,D,R,E$ and for the structural replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each effective real-name request through the route
$$
A\longmapsto S\longmapsto D\longmapsto R\longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\GrzegorczykRealUp$, $\ComputableRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\SpeckerSequenceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\GrzegorczykRealUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite effective real-name surface. It contains no quotient stream equality, selected limit, host real comparison, countable-choice selector, ambient $\RealUp$ completeness witness, or bridge credential.
\end{definition}

\begin{theorem}[Grzegorczyk real NameCert obligations]
\label{thm:grzegorczyk-real-namecert-obligations}
For every accepted $\GrzegorczykRealUp$ carrier $G=(A,S,D,R,E,H,C,P,N)$, the local $\NameCert_{\GrzegorczykRealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the effective approximant, finite StreamName windows, dyadic tolerance ledger, regular rational readback, terminal Real seal, transports, replay, provenance, and local naming rows;
\item modulus-window exactness, requiring each precision request made by the effective approximant row $A$ to be witnessed by the finite window row $S$ before $R$ or $E$ can be consumed;
\item dyadic tolerance stability, requiring the ledger $D$ to preserve the displayed error budget for every transported approximant window and every regular readback cell;
\item RegSeqRat handoff, requiring $R$ to be the only route by which the effective approximant windows become a regular rational real name;
\item RealUp seal non-escape, requiring every $\RealUp$ consumer of $E$ to pass through $A,S,D,R$ and the structural rows $H,C,P,N$ rather than through quotient equality, a selected limit, countable choice, a host real, or ambient completeness.
\end{enumerate}
No Grzegorczyk-real obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:grzegorczyk-real-carrier}. The accepted packet lists exactly the effective approximant, finite windows, dyadic ledger, regular readback, terminal seal, and structural rows.

For modulus-window exactness, read the carrier route from $A$ to $S$. A precision request in $A$ is not exported directly; it is witnessed by the finite $\StreamNameUp$ window row $S$ before any regular readback or Real-facing seal can be inspected.

Dyadic tolerance stability is the next coordinate of the route. The ledger $D$ stores the radii and slack comparisons attached to each displayed window, and the transport row $H$ preserves those cells componentwise while $C$ replays the same finite path.

The RegSeqRat handoff is then forced by row order. The row $R$ appears after the window and tolerance data and before the seal, so a consumer cannot treat the approximant stream as a real name without passing through the regular rational readback.

Finally, RealUp seal non-escape follows from terminality of $E$ and provenance exhaustion in $P,N$. Since the carrier has no further coordinates, every $\RealUp$ consumer factors through $A,S,D,R,E,H,C,P,N$ and receives no quotient stream equality, selected limit, countable-choice source, host real comparison, ambient completeness principle, or bridge credential.
\end{proof}

\begin{theorem}[Grzegorczyk real stream-real seal factorization]
\label{thm:grzegorczyk-real-stream-real-seal-factorization}
For every accepted $\GrzegorczykRealUp$ carrier $G=(A,S,D,R,E,H,C,P,N)$, every $\RealUp$ consumer of the seal $E$ factors through the displayed effective approximant, finite stream window, dyadic tolerance, regular readback, and seal rows:
$$
A\longmapsto S\longmapsto D\longmapsto R\longmapsto E .
$$
In particular the consumer cannot bypass the $\ComputableRealUp$ approximant row, cannot replace $S$ by a quotient stream, cannot replace $R$ by a selected limit, and cannot read $E$ as an ambient completeness witness.
\end{theorem}
\begin{proof}
Start with a seal-facing request. Carrier projection exposes $E$ only as the terminal coordinate of the displayed Grzegorczyk-real route, not as an independently completed real object.

Trace the route backward from $E$. The seal is downstream of $R$, the regular readback is downstream of the dyadic tolerance ledger $D$, and the ledger is attached to finite windows $S$ requested by the effective approximant row $A$.

The structural rows preserve this route. Componentwise $\hsame$ transport in $H$ keeps the same approximant, window, tolerance, readback, and seal coordinates, while the $\Cont$ replay row $C$ records that each consumer request follows the same finite path.

The provenance and local naming rows $P,N$ name no additional real-completion principle. Thus every seal consumer factors through $A,S,D,R,E$ together with $H,C,P,N$, and no excluded quotient, selection, host-real, countable-choice, ambient-completeness, or bridge route is available.
\end{proof}

\closureat{GrzegorczykRealUp}{seedStr}

\begin{closurestatus}{\GrzegorczykRealUp}
  \constructivestory{A $\GrzegorczykRealUp$ packet is generated from an effective approximant row, finite StreamName windows, DyadicRatCore tolerance rows, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:grzegorczyk-real-carrier}, \autoref{thm:grzegorczyk-real-namecert-obligations}, and \autoref{thm:grzegorczyk-real-stream-real-seal-factorization} seed the effective real-name boundary between computable approximants, finite stream windows, regular rational readback, and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, host real comparison, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus-window exactness, dyadic tolerance stability, RegSeqRat handoff, RealUp seal non-escape, and a Lean carrier/obligation formalization for BEDC.Derived.GrzegorczykRealUp.}
\end{closurestatus}
