\chapter{A Concrete Naming Certificate for $\LesserLimitedOmniscienceUp$}
\label{ch:concrete-instances-lesser-limited-omniscience-namecert}
\origin{human}

Following Brouwer, Bishop--Bridges, and Troelstra--van Dalen constructive analysis, the $\LesserLimitedOmniscienceUp$ packet records the finite boundary at which a two-alternative inspection may be named without accepting lesser limited omniscience as a global principle. It is read beside the Specker obstruction of \autoref{ch:concrete-instances-speckersequence-namecert}, the Markov boundary of \autoref{ch:concrete-instances-markov-principle-boundary-namecert}, the fan-theorem boundary of \autoref{ch:concrete-instances-fantheorem-namecert}, the stream schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a Real/Completion boundary object: it displays the finite rows a consumer may inspect before any $\RealUp$ seal read and refuses every route from those rows to LPO, trichotomy, quotient real equality, selected limits, countable choice, open-cover compactness, or ambient real completeness.

\begin{definition}[Lesser limited omniscience carrier]
\label{def:lesser-limited-omniscience-carrier}
A $\LesserLimitedOmniscienceUp$ carrier is a finite $\BHist$ packet
$$
L=(A_0,A_1,S,R,D,E,W,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $A_0$ is the first alternative row, naming the finite schedule branch on which the left disjunct would be certified if the inspected evidence reaches it.
\item $A_1$ is the second alternative row, naming the finite schedule branch on which the right disjunct would be certified if the inspected evidence reaches it.
\item $S$ is the $\StreamNameUp$ schedule row listing the finite stream requests admitted by the boundary.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational values actually inspected from $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger naming the dyadic radii, endpoint comparisons, and finite margin rows used to keep $A_0$ and $A_1$ apart.
\item $E$ is the $\RealUp$ seal reached only after the rows $A_0,A_1,S,R,D$ have been displayed.
\item $W$ is the refusal/witness row: it either records the displayed finite alternative witnessed by the inspected packet or records the finite refusal that no global LLPO principle is exported.
\item $H$ stores componentwise $\hsame$ transport for the two alternative rows, stream schedule, regular-rational readback, dyadic ledger, real seal, witness/refusal row, continuation row, provenance row, and local name.
\item $C$ stores $\Cont$ replay from finite stream requests through $R$ and $D$, then through the alternative rows $A_0,A_1$, and finally into the sealed real-facing row $W$.
\item $P$ records $\Pkg$ provenance over $\LesserLimitedOmniscienceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\SpeckerSequenceUp$, $\MarkovPrincipleBoundaryUp$, $\FanTheoremUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LesserLimitedOmniscienceUp}$ row.
\end{enumerate}
The carrier has no coordinate for imported LLPO, LPO, trichotomy, countable choice, quotient stream equality, quotient real equality, selected limits, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.LesserLimitedOmniscienceUp.LesserLimitedOmniscienceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Lesser limited omniscience NameCert obligations]
\label{thm:lesser-limited-omniscience-namecert-obligations}
For every accepted $\LesserLimitedOmniscienceUp$ carrier $L=(A_0,A_1,S,R,D,E,W,H,C,P,N)$, the local $\NameCert_{\LesserLimitedOmniscienceUp}$ surface consists exactly of the following five finite obligations:
\begin{enumerate}
\item carrier exposure for the two alternative rows, StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, refusal/witness row, transport, continuation, package, and local naming rows;
\item classifier componentwise transport, requiring every comparison between packets to use the $\hsame$ rows stored in $H$ coordinate by coordinate;
\item alternative-row disjointness, requiring any accepted left/right alternative to cite the displayed dyadic separation and finite margin data in $D$;
\item real-seal handoff, requiring every Real/Completion consumer to reach $E$ only after the schedule, readback, ledger, alternatives, and refusal/witness row have been displayed;
\item ledger nonescape from imported LLPO, LPO, trichotomy, countable choice, quotient stream equality, quotient real equality, selected limits, open-cover compactness, and ambient real completeness.
\end{enumerate}
No NameCert obligation is stored outside these five rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:lesser-limited-omniscience-carrier}. The visible data are the two alternative rows $A_0,A_1$, the schedule $S$, readback $R$, tolerance ledger $D$, terminal seal $E$, refusal/witness row $W$, and structural rows $H,C,P,N$.

Classifier transport is componentwise because the packet offers no aggregate classifier coordinate. A comparison of accepted packets must therefore use the displayed $\hsame$ rows in $H$ for each alternative, readback, ledger, seal, witness, replay, provenance, and local name.

Alternative-row disjointness is forced by the tolerance ledger $D$. A branch may expose an alternative only by naming a dyadic radius, endpoint comparison, and finite margin row already present in the ledger; otherwise $W$ records only the refusal of a global disjunctive principle.

The real-seal handoff is downstream of $E$, and the replay path is supplied by $C$. Since the carrier contains no coordinate for imported LLPO, LPO, trichotomy, choice, quotient equality, selected limits, open-cover compactness, or ambient completeness, those principles cannot be exported through the local $\NameCert_{\LesserLimitedOmniscienceUp}$ row.
\end{proof}

\begin{theorem}[Lesser limited omniscience nonescape]
\label{thm:lesser-limited-omniscience-nonescape}
Every Real/Completion consumer of an accepted $\LesserLimitedOmniscienceUp$ packet receives only the two displayed alternative rows, finite schedule, regular-rational readback, dyadic ledger, terminal real seal, refusal/witness row, componentwise transport, continuation replay, provenance, and local NameCert row. It receives no imported LLPO, no LPO, no trichotomy, no countable choice, no quotient stream equality, no quotient real equality, no selected limit, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Let a Real/Completion consumer accept $L=(A_0,A_1,S,R,D,E,W,H,C,P,N)$. By \autoref{def:lesser-limited-omniscience-carrier}, the only real-facing coordinate is the seal $E$, and that seal is reached after the two alternatives, stream schedule, regular-rational readback, dyadic ledger, and refusal/witness row have been displayed.

The consumer's branch information is therefore finite. It can replay the schedule through $R$, cite only dyadic tolerance rows from $D$, and transport the two alternatives through $H$ and $C$.

No omitted semi-classical or completion principle is a coordinate of the packet. Thus factorization through the displayed rows cannot export imported LLPO, LPO, trichotomy, countable choice, quotient stream equality, quotient real equality, selected limits, or ambient real completeness.
\end{proof}

\begin{theorem}[Specker, Markov, and fan boundary factorization]
\label{thm:lesser-limited-omniscience-specker-markov-fan-boundary}
Every $\SpeckerSequenceUp$, $\MarkovPrincipleBoundaryUp$, or $\FanTheoremUp$ consumer using an accepted $\LesserLimitedOmniscienceUp$ packet factors through the displayed finite rows
$$
A_0,A_1,S,R,D,E,W,H,C,P,N
$$
before any $\RealUp$ seal read.
\end{theorem}
\begin{proof}
The carrier names the two alternatives and the finite stream schedule before the real seal. Thus a Specker consumer can inspect only the displayed obstruction-facing schedule and readback rows $S,R$ before it reaches $E$.

A Markov-boundary consumer reaches its negative-evidence boundary through the same finite rows. It may cite $W$ as a refusal/witness row, but $W$ is downstream of $A_0,A_1,S,R,D$ and therefore cannot introduce an unlisted principle.

A fan-theorem consumer likewise receives only the finite branch rows and the dyadic ledger before the seal. Componentwise transport in $H$ and continuation replay in $C$ preserve this route, while $P$ and $N$ repackage the same finite data as the local NameCert surface.
\end{proof}

\closureat{LesserLimitedOmniscienceUp}{seedStr}

\begin{closurestatus}{\LesserLimitedOmniscienceUp}
  \constructivestory{A $\LesserLimitedOmniscienceUp$ packet is generated from two disjoint alternative rows, a StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, refusal/witness row, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lesser-limited-omniscience-carrier}, \autoref{thm:lesser-limited-omniscience-namecert-obligations}, \autoref{thm:lesser-limited-omniscience-nonescape}, and \autoref{thm:lesser-limited-omniscience-specker-markov-fan-boundary} seed the finite LLPO boundary for Real/Completion consumers.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.LesserLimitedOmniscienceUp.LesserLimitedOmniscienceTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim LLPO as a global principle, LPO, trichotomy, countable choice, quotient real equality, selected limits, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, classifier componentwise transport, alternative-row disjointness, real-seal handoff, Specker/Markov/Fan factorization, and ledger nonescape for the same finite packet.}
\end{closurestatus}
