\chapter{A Concrete Naming Certificate for $\DenseImageCompletionUp$}
\label{ch:concrete-instances-dense-image-completion-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and dense embeddings, the $\DenseImageCompletionUp$ packet records the finite L10 interface by which displayed source points approximate completion-facing consumers through the already named entry map of \autoref{ch:concrete-instances-cauchy-completion-embedding-namecert}. It sits between the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only finite approximation rows: it does not construct quotient completions, select limits, identify host objects, invoke countable choice, use ambient $\RealUp$ completeness, or claim bridge checking.

\begin{definition}[Dense image completion carrier]
\label{def:dense-image-completion-carrier}
A $\DenseImageCompletionUp$ carrier is a finite $\BHist$ packet
$$
G=(X,E,A,M,R,S,D,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the displayed source metric point row whose finite observations are available before any completion-facing read.
\item $E$ is the $\CauchyCompletionEmbeddingUp$ entry row that exposes the source point as displayed completion-entry data.
\item $A$ is the dense approximation witness row, recording the inspected completion request, the displayed source point chosen for that request, and the finite tolerance comparison between them.
\item $M$ is the $\MetricCompletionUp$ row consumed by completion-facing clients after $X,E,A$ have been displayed.
\item $R$ is the $\RegSeqRatUp$ readback row used to answer numerical tolerance requests from the dense approximation witness.
\item $S$ is the $\StreamNameUp$ finite-window row through which the source and approximation reads are exposed to consumers.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, storing the dyadic radius, slack comparison, and budget consumed by $A,R,S,M$.
\item $H$ records componentwise $\hsame$ transport for the source point, embedding row, approximation witness, metric-completion row, regular readback, stream windows, dyadic ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
X \longmapsto E \longmapsto A \longmapsto S \longmapsto R,D \longmapsto M .
$$
\item $P$ is the $\Pkg$ provenance over $\DenseImageCompletionUp$, $\CauchyCompletionEmbeddingUp$, $\MetricCompletionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DenseImageCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected limits, host equality of completed objects, countable-choice schedules, ambient $\RealUp$ completeness, or bridge credentials.
\end{definition}
\leanchecked{BEDC.Derived.DenseImageCompletionUp.DenseImageCompletionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Dense image completion NameCert obligations]
\label{thm:dense-image-completion-namecert-obligations}
For an accepted $\DenseImageCompletionUp$ carrier $G=(X,E,A,M,R,S,D,H,C,P,N)$, the local $\NameCert_{\DenseImageCompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source point, completion embedding row, dense approximation witness, metric-completion row, regular readback, stream windows, dyadic tolerance ledger, transport, replay, provenance, and local naming rows;
\item entry-before-approximation exposure, requiring every completion-facing request to read $X$ through $E$ before the dense witness $A$ can be consumed;
\item dense approximation locality, requiring $A$ to bind one displayed completion request, one displayed source row, and one dyadic tolerance budget from $D$;
\item readback readiness, requiring each numerical approximation claim to pass through $S$ and $R$ before it is offered to the metric-completion row $M$;
\item classifier stability, requiring transported packets with the same displayed $X,E,A,M,R,S,D$ route to be identified through the carried $\hsame$ and $\Cont$ data;
\item ledger non-escape, stating that no quotient completion equality, selected limit, host equality, countable-choice schedule, ambient $\RealUp$ completeness theorem, or bridge credential is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dense-image-completion-carrier}. The tuple lists exactly the source point, completion embedding, dense witness, metric-completion, readback, stream, dyadic ledger, transport, replay, provenance, and local naming rows.

Entry-before-approximation exposure follows because $E$ is the only row connecting the displayed source point $X$ to the completion-facing surface. A consumer cannot inspect a dense witness before the source point has been routed through this entry row.

Dense approximation locality is the projection to $A$ together with the tolerance ledger $D$. The witness records a finite request, a displayed source point, and a dyadic budget; it does not create a host completion object or choose a limit.

Readback readiness uses $S$ and $R$. The stream row exposes the finite windows inspected by the approximation witness, and the regular readback row is the only numerical route offered to the metric-completion consumer $M$.

Classifier stability is componentwise transport along $H$ followed by replay through $C$. Since $P$ and $N$ only source and name the same finite packet, the excluded quotient, selected-limit, host-equality, choice, ambient-completeness, and bridge data have no carrier row from which they could be projected.
\end{proof}

\begin{theorem}[Dense image completion approximation route]
\label{thm:dense-image-completion-approximation-route}
Let $G=(X,E,A,M,R,S,D,H,C,P,N)$ be an accepted $\DenseImageCompletionUp$ carrier. Every completion-facing approximation exported by $G$ factors through the finite route
$$
X \longmapsto E \longmapsto A \longmapsto S \longmapsto R,D \longmapsto M \longmapsto H,C,P,N .
$$
Thus the dense-image statement is a displayed BEDC handoff from source rows to metric-completion consumers, not quotient completion equality, not a selected limit, not host equality, and not an appeal to countable choice or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a completion-facing approximation request. Projection gives the source row $X$ and the embedding row $E$, so the request first enters the completion interface through the same finite entry surface named by \autoref{ch:concrete-instances-cauchy-completion-embedding-namecert}.

The dense witness $A$ is then read with its dyadic budget $D$. This records a displayed source point near the inspected completion request at the stated finite tolerance.

The consumer next reads $S$ and $R$. The stream row provides the finite windows behind the approximation, and the regular rational readback supplies the numerical data passed downstream.

Only after those rows are fixed does the route reach $M$, the metric-completion row. Transport, replay, provenance, and local naming through $H,C,P,N$ preserve the same displayed route and add no quotient, selected-limit, host-equality, choice, ambient-completeness, or bridge credential.
\end{proof}

\begin{theorem}[Dense image completion ledger exhaustion]
\label{thm:dense-image-completion-ledger-exhaustion}
For an accepted $\DenseImageCompletionUp$ carrier $G=(X,E,A,M,R,S,D,H,C,P,N)$, every tolerance-facing, readback-facing, or metric-completion-facing read exported by $G$ is generated by the rows named in \autoref{def:dense-image-completion-carrier}. In particular, the packet exports no quotient completion equality, no selected limit, no host equality, no countable-choice schedule, no ambient $\RealUp$ completeness theorem, and no bridge-checking credential.
\end{theorem}
\begin{proof}
Project the accepted carrier. A tolerance-facing read must pass through $D$, and the only rows that can consume that dyadic budget are the dense witness $A$, the stream windows $S$, the regular readback $R$, and the metric-completion row $M$.

A readback-facing consumer is similarly confined to $S$ and $R$. The stream row fixes the finite observation window, while the regular readback row records the numerical approximation produced from that window and the dyadic ledger.

A metric-completion-facing consumer must pass through $X,E,A,S,R,D$ before $M$ is available. The completion row is therefore downstream of the displayed source entry and the finite dense-witness ledger.

The structural rows $H,C,P,N$ transport, replay, source, and name only the same route. Since the tuple has no other coordinates, route exhaustion rules out quotient completion equality, selected limits, host equality, countable choice, ambient $\RealUp$ completeness, and bridge checking.
\end{proof}

\closureat{DenseImageCompletionUp}{seedStr}

\begin{closurestatus}{\DenseImageCompletionUp}
  \constructivestory{A $\DenseImageCompletionUp$ packet is generated from a displayed source metric point, a CauchyCompletionEmbedding entry row, a dense approximation witness, a MetricCompletion row, RegSeqRat readback, StreamName finite windows, a DyadicRatCore tolerance ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dense-image-completion-carrier}, \autoref{thm:dense-image-completion-namecert-obligations}, \autoref{thm:dense-image-completion-approximation-route}, and \autoref{thm:dense-image-completion-ledger-exhaustion} seed the finite dense-image interface between completion embeddings and L10 completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected limits, host equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, entry-before-approximation exposure, dense approximation locality, readback readiness, classifier stability, ledger exhaustion, and a Lean carrier/obligation formalization for BEDC.Derived.DenseImageCompletionUp.}
\end{closurestatus}
