\chapter{A Concrete Naming Certificate for $\ArithmeticGeometricMeanUp$}
\label{ch:concrete-instances-arithmetic-geometric-mean-namecert}
\origin{human}

Following Gauss' arithmetic-geometric mean and Bishop--Bridges constructive real analysis, the $\ArithmeticGeometricMeanUp$ packet records the finite mean-iteration route available for two displayed positive real names. It sits after the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the absolute-value boundary of \autoref{ch:concrete-instances-real-abs-namecert}, the constructive square-root service of \autoref{ch:concrete-instances-regular-cauchy-square-root-namecert}, the dyadic tolerance scale of \autoref{ch:concrete-instances-dyadic-tolerance-scale-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}. The packet gives L10 Real and Completion consumers one visible certificate for arithmetic and geometric mean iteration while withholding host real equality, quotient Cauchy equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, and standard-bridge data.

\begin{definition}[Arithmetic-geometric mean carrier]
\label{def:arithmetic-geometric-mean-carrier}
An $\ArithmeticGeometricMeanUp$ carrier is a finite $\BHist$ packet
$$
M=(X,Y,A,G,D,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are positive $\RealUp$ endpoint rows, each exposing a terminal real-name seal, positivity witness, finite $\StreamNameUp$ windows, and $\RegSeqRatUp$ readback data.
\item $A$ is the arithmetic midpoint row, recording the displayed half-sum operation from the current endpoint rows before any downstream seal is consumed.
\item $G$ is the geometric midpoint row, routing the displayed product of the two positive endpoint rows through $\RegularCauchySquareRootUp$ and the accompanying square-root readback service.
\item $D$ is the $\DyadicToleranceScaleUp$ ledger, storing the precision scale, dyadic radii, comparison slack, and budget cells used by the midpoint and square-root rows.
\item $S$ is the finite $\StreamNameUp$ window row selected for the current arithmetic and geometric midpoint requests.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the selected windows and dyadic tolerance ledger.
\item $E$ is the $\RealUp$ seal row for the exported mean-iteration state, reachable only after $X,Y,A,G,D,S,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the endpoint rows, arithmetic midpoint, geometric midpoint, tolerance ledger, finite windows, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of each accepted precision request through
$$
X,Y\longmapsto A,G\longmapsto D\longmapsto S\longmapsto Q\longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\ArithmeticGeometricMeanUp$, $\RealUp$, $\RealAbsUp$, $\RegularCauchySquareRootUp$, $\DyadicToleranceScaleUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ArithmeticGeometricMeanUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,A,G,D,S,Q,E,H,C,P,N$. It has no coordinate for host real equality, quotient Cauchy equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean evidence, or standard-bridge data.
\end{definition}

\begin{theorem}[Arithmetic-geometric mean NameCert obligations]
\label{thm:arithmetic-geometric-mean-namecert-obligations}
For every accepted $\ArithmeticGeometricMeanUp$ carrier
$$
M=(X,Y,A,G,D,S,Q,E,H,C,P,N),
$$
the local $\NameCert_{\ArithmeticGeometricMeanUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the two positive $\RealUp$ endpoint rows $X,Y$, the arithmetic midpoint row $A$, the geometric midpoint and square-root row $G$, the $\DyadicToleranceScaleUp$ ledger $D$, the $\StreamNameUp$ windows $S$, the $\RegSeqRatUp$ readback $Q$, the terminal $\RealUp$ seal $E$, and the structural rows $H,C,P,N$;
\item positivity routing, requiring the geometric midpoint row to read the positive endpoint data in $X,Y$ before invoking the square-root service;
\item midpoint discipline, requiring $A$ and $G$ to be the only arithmetic and geometric mean rows consumed by the exported iteration state;
\item tolerance accounting, requiring $D$ to store exactly the dyadic scale, radii, comparison slack, and budget cells consumed by $A,G,S,Q,E$;
\item window and readback handoff, requiring every precision request to pass through $S$ and $Q$ before the Real seal $E$ is read;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$;
\item non-escape for host real equality, quotient Cauchy equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, and standard-bridge data.
\end{enumerate}
No arithmetic-geometric-mean obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:arithmetic-geometric-mean-carrier}. The two endpoint rows, arithmetic midpoint, geometric midpoint, tolerance ledger, finite windows, readback, and Real seal are the only analytic coordinates, while $H,C,P,N$ are the only structural coordinates.

The positivity route is forced by the displayed tuple. The geometric midpoint row $G$ reads the positive endpoint data from $X$ and $Y$, then uses the square-root service named in the provenance row; there is no detached square-root coordinate available to the classifier.

The tolerance and readback rows are downstream of the midpoint rows. The ledger $D$ stores the dyadic scale and slack data consumed by $A$ and $G$, the window row $S$ exposes the finite observations, and $Q$ is the regular rational readback that precedes the terminal seal.

Finally, $H,C,P,N$ transport, replay, source, and name the same finite route. Since none of the excluded host, quotient, choice, completeness, verification, or bridge objects appears as a carrier coordinate, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Arithmetic-geometric mean Real-seal handoff]
\label{thm:arithmetic-geometric-mean-real-seal-handoff}
Every Real or Completion consumer of an accepted $\ArithmeticGeometricMeanUp$ carrier reaches the exported mean-iteration seal only through the displayed route
$$
X,Y\longmapsto A,G\longmapsto D\longmapsto S\longmapsto Q\longmapsto E\longmapsto H,C,P,N .
$$
Consequently the consumer receives two positive Real endpoint rows, an arithmetic midpoint row, a geometric midpoint routed through $\RegularCauchySquareRootUp$, a dyadic tolerance ledger, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, a terminal $\RealUp$ seal, componentwise transport, continuation replay, provenance, and local naming. The handoff supplies no host real equality, quotient Cauchy equality, selected limit, trichotomy witness, countable-choice selector, ambient $\RealUp$ completeness principle, Lean evidence, or standard bridge.
\end{theorem}
\begin{proof}
Start with an accepted carrier $M=(X,Y,A,G,D,S,Q,E,H,C,P,N)$. The endpoint rows $X$ and $Y$ are the only sources for the two positive real names, so every accepted midpoint request begins with displayed Real seals and their finite observation data.

The arithmetic midpoint row $A$ records the half-sum route. The geometric midpoint row $G$ records the product-and-square-root route, and the square-root service is read only through the displayed positive endpoint data and the provenance named by the same carrier.

The dyadic tolerance row $D$ then fixes the precision scale consumed by both midpoint rows. The finite windows $S$ and regular rational readback $Q$ are the only observation rows from which a downstream consumer can proceed to the terminal seal $E$.

Componentwise transport and replay through $H$ and $C$, together with provenance and local naming in $P,N$, preserve the same route. The carrier contains no coordinate for the excluded host, quotient, choice, completeness, verification, or bridge data, so the displayed handoff is exhaustive.
\end{proof}

\falsifiablePrediction{Every $\ArithmeticGeometricMeanUp$ precision read factors through two positive RealUp endpoint rows, arithmetic midpoint data, geometric midpoint and square-root data, a DyadicToleranceScale ledger, finite StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{real, real-abs, regular-cauchy-square-root, dyadic-tolerance-scale, streamname, regseqrat: $\ArithmeticGeometricMeanUp$ is not bijective to any listed sibling because it jointly carries two positive endpoint rows, arithmetic midpoint routing, geometric midpoint square-root routing, dyadic tolerance accounting, finite window selection, regular readback, terminal Real-seal handoff, transport, replay, provenance, and local naming.}

\closureat{ArithmeticGeometricMeanUp}{seedStr}

\begin{closurestatus}{\ArithmeticGeometricMeanUp}
  \constructivestory{An $\ArithmeticGeometricMeanUp$ packet is generated from two positive RealUp endpoint rows, one arithmetic midpoint row, one geometric midpoint routed through RegularCauchySquareRoot, a DyadicToleranceScale ledger, finite StreamName windows, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:arithmetic-geometric-mean-carrier}, \autoref{thm:arithmetic-geometric-mean-namecert-obligations}, and \autoref{thm:arithmetic-geometric-mean-real-seal-handoff} seed the finite constructive arithmetic-geometric mean route for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real equality, quotient Cauchy equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, positivity routing, midpoint discipline, tolerance accounting, window/readback handoff, Real-seal non-escape, transport/replay/provenance coverage, and exclusion for BEDC.Derived.ArithmeticGeometricMeanUp.}
\end{closurestatus}
