\chapter{A Concrete Naming Certificate for $\CauchyFilterModulusTransferUp$}
\label{ch:concrete-instances-cauchy-filter-modulus-transfer-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy completions, and Kelley and Bourbaki on filter bases, the $\CauchyFilterModulusTransferUp$ packet names the finite bridge by which located Cauchy-filter requests are regularized into modulus rows before a completion-facing consumer reads a real seal. It sits between the located-filter source of \autoref{ch:concrete-instances-located-cauchy-filter-namecert}, the finite base route of \autoref{ch:concrete-instances-cauchy-filter-base-namecert}, the common-refinement operation of \autoref{ch:concrete-instances-cauchy-filter-meet-namecert}, and the ideal-completion boundary of \autoref{ch:concrete-instances-rounded-ideal-completion-namecert}. The downstream L10 route reads finite windows through \autoref{ch:concrete-instances-streamname-namecert}, regular rational rows through \autoref{ch:concrete-instances-regseqrat-namecert}, dyadic tolerances through \autoref{ch:concrete-instances-dyadicratcore-namecert}, and terminal seals through \autoref{ch:concrete-instances-real-namecert}. The packet is a finite transfer surface from filter-base evidence to regular Cauchy modulus data; it is not a quotient filter, selected limit, countable-choice schedule, host equality comparison, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.

\begin{definition}[Cauchy filter modulus transfer carrier]
\label{def:cauchy-filter-modulus-transfer-carrier}
A $\CauchyFilterModulusTransferUp$ carrier is a finite $\BHist$ packet
$$
T=(F,B,L,J,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the Cauchy filter source row. It records the displayed $\CauchyFilterUp$ request surface whose precision requests are to be regularized.
\item $B$ is the $\CauchyFilterBaseUp$ basis row. It exposes finite base indices, entourage requests, directed-refinement reads, and Cauchy readiness rows used by the source filter.
\item $L$ is the located-tail row. It records the $\LocatedCauchyFilterUp$ evidence that every requested tail can be inspected by a located finite base request before any regular modulus row is exported.
\item $J$ is the common-refinement row. It reads the $\CauchyFilterMeetUp$ operation and names, for each requested tolerance and each located tail request, a displayed refinement accepted by both the filter source and the basis route.
\item $S$ is the $\StreamNameUp$ window row reached only after $F,B,L,J$ have been displayed.
\item $R$ is the $\RegSeqRatUp$ handoff row that repacks the accepted window route as a regular rational sequence row.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It records the requested dyadic scale, the smaller scale selected by the located-tail row, and the budget comparison used to certify regular Cauchy control.
\item $E$ is the terminal $\RealUp$ seal boundary. It is visible only after the filter source, basis route, located-tail row, common-refinement row, window row, regular readback row, and dyadic ledger have been replayed.
\item $H$ records componentwise $\hsame$ transport for the source filter, basis row, located-tail row, common-refinement row, window, regular readback, dyadic tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a filter request through $F,B,L,J,S,R,D,E$ in that order.
\item $P$ is the $\Pkg$ provenance over $\CauchyFilterModulusTransferUp$, $\CauchyFilterUp$, $\CauchyFilterBaseUp$, $\LocatedCauchyFilterUp$, $\CauchyFilterMeetUp$, $\RoundedIdealCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyFilterModulusTransferUp}$ row.
\end{enumerate}
The classifier compares accepted transfer packets only through the displayed route
$$
F,B,L,J \longmapsto S,R,D,E \longmapsto H,C,P,N .
$$
No carrier coordinate stores a quotient filter, selected limit, countable-choice schedule, host equality of filter values, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.
\end{definition}

\begin{theorem}[Cauchy filter modulus transfer NameCert obligations]
\label{thm:cauchy-filter-modulus-transfer-namecert-obligations}
For every accepted $\CauchyFilterModulusTransferUp$ carrier
$$
T=(F,B,L,J,S,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyFilterModulusTransferUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the Cauchy filter source, basis row, located-tail row, common-refinement row, window row, regular rational handoff, dyadic tolerance ledger, terminal seal, transport, replay, provenance, and local naming row;
\item source-to-basis routing, requiring each displayed filter request in $F$ to read its finite base witness from $B$ before the located-tail row can be inspected;
\item located-tail regularization, requiring each requested precision to pass through $L$ and name a finite tail request that is small enough for regular Cauchy control;
\item common-refinement coverage, requiring $J$ to refine the basis request and located-tail request over the same filter source before any window, readback, tolerance, or seal row is visible;
\item finite modulus handoff, requiring the route from $J$ to pass through $S,R,D$ before reaching the terminal $\RealUp$ seal boundary $E$;
\item transport and replay stability, requiring $H$ and $C$ to preserve the row order $F,B,L,J,S,R,D,E$ under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item provenance exhaustion, requiring $P,N$ to name only this finite transfer route and to export no quotient filter, selected limit, countable-choice schedule, host equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-filter-modulus-transfer-carrier}. The projection exposes exactly the filter source, basis route, located-tail row, common-refinement row, finite window, regular readback, dyadic ledger, terminal seal, and structural rows $H,C,P,N$.

The source-to-basis route is fixed by row order. A transfer request first reads $F$, then reads the finite base index, entourage request, and readiness evidence supplied by $B$ before any located-tail regularization is available.

Located-tail regularization is the role of $L$. For a requested precision, $L$ names the displayed tail request and records the finite locatedness evidence showing that this request is small enough for the regular Cauchy handoff.

The common-refinement row $J$ then aligns the basis request with the located-tail request. Since $J$ is a carrier coordinate, the refinement is finite data in the packet rather than an ambient filter lattice principle.

The modulus handoff is replayed by $C$ through $S,R,D$ before $E$ can be inspected. Componentwise transport in $H$ preserves the same rows, while $P,N$ source and name only this packet; therefore the excluded quotient, choice, host-equality, real-completeness, Lean-verification, and bridge-checking data are outside the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy filter modulus transfer basis regularization]
\label{thm:cauchy-filter-modulus-transfer-basis-regularization}
Let
$$
T=(F,B,L,J,S,R,D,E,H,C,P,N)
$$
be an accepted $\CauchyFilterModulusTransferUp$ carrier. Every displayed filter precision request factors through a finite regularization route
$$
F \longmapsto B \longmapsto L \longmapsto J \longmapsto S,R,D .
$$
Consequently the packet exports a regular Cauchy modulus row only after a source filter request has been witnessed by a basis row, located as a finite tail request, refined against that basis request, and checked by the displayed window, regular readback, and dyadic tolerance ledger.
\end{theorem}
\begin{proof}
Start with a displayed precision request in $F$. The carrier exposes no direct regular-modulus coordinate, so the request must first be read through the basis row $B$.

The located-tail row $L$ supplies the finite tail request attached to the same precision. This step is constructive: the row contains the inspected tail witness and not a selected limit or a countable-choice schedule.

Next read $J$. It names the common refinement of the basis request and the located-tail request, so the regularization route remains attached to one displayed filter source.

Finally replay the finite observation rows $S,R,D$. The window row supplies the finite observations, the regular rational row repacks them as $\RegSeqRatUp$ data, and the dyadic ledger records the tolerance comparison needed for regular Cauchy control. Thus the regular modulus row is exported only through the displayed route.
\end{proof}

\begin{theorem}[Cauchy filter modulus transfer real seal boundary]
\label{thm:cauchy-filter-modulus-transfer-real-seal-boundary}
Every completion-facing or $\RealUp$-facing consumer of an accepted $\CauchyFilterModulusTransferUp$ carrier
$$
T=(F,B,L,J,S,R,D,E,H,C,P,N)
$$
reaches the terminal seal $E$ only through the finite route
$$
F,B,L,J,S,R,D \longmapsto E \longmapsto H,C,P,N .
$$
In particular, the consumer receives a filter source row, basis row, located-tail row, common-refinement row, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, componentwise transport, continuation replay, provenance, and local naming. It receives no selected limit, quotient filter, countable-choice schedule, host equality, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.
\end{theorem}
\begin{proof}
Begin with a completion-facing or $\RealUp$-facing read named by $P$. Carrier projection restricts the consumer to the rows displayed in \autoref{def:cauchy-filter-modulus-transfer-carrier}.

Apply \autoref{thm:cauchy-filter-modulus-transfer-basis-regularization}. The precision request must pass through $F,B,L,J,S,R,D$ before a regular modulus row is available.

The seal row $E$ is placed after that regularization route. A consumer therefore sees the terminal $\RealUp$ boundary only after the source filter, basis evidence, located tail, common refinement, finite windows, regular rational handoff, and dyadic tolerance ledger have all been replayed.

The structural rows do not add analytic content. The transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$ preserve and name the displayed route, so selected limits, quotient filters, choice schedules, host equality, ambient real completeness, Lean verification, and bridge checking cannot enter through the seal boundary.
\end{proof}

\begin{closurestatus}{\CauchyFilterModulusTransferUp}
  \constructivestory{A $\CauchyFilterModulusTransferUp$ packet is generated from a CauchyFilter source row, a CauchyFilterBase basis row, a LocatedCauchyFilter tail row, a CauchyFilterMeet common-refinement row, StreamName windows, RegSeqRat handoff, DyadicRatCore tolerances, a RealUp seal boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-filter-modulus-transfer-carrier}, \autoref{thm:cauchy-filter-modulus-transfer-namecert-obligations}, \autoref{thm:cauchy-filter-modulus-transfer-basis-regularization}, and \autoref{thm:cauchy-filter-modulus-transfer-real-seal-boundary} seed the finite bridge from located Cauchy-filter evidence and filter-base requests to regular Cauchy modulus rows before the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient filters, countable choice, host equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-to-basis routing, located-tail regularization, common-refinement coverage, finite modulus handoff, Real seal boundary, transport, replay, provenance, and local naming for BEDC.Derived.CauchyFilterModulusTransferUp.}
\end{closurestatus}
