\chapter{A Concrete Naming Certificate for $\BishopIntervalCompletionUp$}
\label{ch:concrete-instances-bishop-interval-completion-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopIntervalCompletionUp$ packet records constructive completion of an interval object by finite rational enclosure data and regular real-name readback. It sits after the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the located interval boundary of \autoref{ch:concrete-instances-locatedinterval-namecert}, the rational interval endpoint ledger of \autoref{ch:concrete-instances-rationalinterval-namecert}, and the real interval enclosure route of \autoref{ch:concrete-instances-real-interval-enclosure-namecert}. The packet gives the L10 Real and Completion phase a finite interval-completion certificate while refusing quotient completion, selected limits, countable choice, trichotomy, host real equality, and ambient $\RealUp$ completeness.

\begin{definition}[Bishop interval completion carrier]
\label{def:bishop-interval-completion-carrier}
A $\BishopIntervalCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(I,S,Q,D,E,L,U,A,R,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the source $\RationalIntervalUp$ or $\LocatedIntervalUp$ endpoint row whose lower and upper rational endpoints are admitted before any real-name seal is read.
\item $S$ is the $\StreamNameUp$ finite-window schedule opened for the interval-completion request.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the same window schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger containing the dyadic radius, endpoint scale, and comparison rows used by the completion window.
\item $E$ is the $\RealIntervalEnclosureUp$ row that displays a lower and upper enclosure around the candidate completed interval endpoint data.
\item $L$ and $U$ are the displayed lower and upper completion-bound rows, read from the source interval and the enclosure row rather than from host endpoint values.
\item $A$ is the interval admission row saying that the readback $Q$ with tolerance ledger $D$ lies inside the displayed enclosure $E$ and respects the lower and upper completion bounds.
\item $R$ is the terminal $\RealUp$ seal row reached only after $I,S,Q,D,E,L,U,A$ have been displayed.
\item $T$ records the interval-completion route ledger from rational endpoint data to located interval data, then to real interval enclosure data, and finally to the terminal real-name seal.
\item $H$ records componentwise $\hsame$ transport for all displayed rows of the packet.
\item $C$ records displayed $\Cont$ replay from a requested completion read through $I,S,Q,D,E,L,U,A,R,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopIntervalCompletionUp$, $\RationalIntervalUp$, $\LocatedIntervalUp$, $\RealIntervalEnclosureUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopIntervalCompletionUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite constructive interval-completion packet. It has no coordinate for quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, or a host interval representative.
\end{definition}
\leanchecked{BEDC.Derived.BishopIntervalCompletionUp.BishopIntervalCompletionTasteGate\_single\_carrier\_alignment}

\begin{definition}[Bishop interval completion classifier]
\label{def:bishop-interval-completion-classifier}
The classifier for accepted $\BishopIntervalCompletionUp$ carriers compares two packets only by componentwise agreement of the displayed source interval row, stream window, regular rational readback, dyadic tolerance ledger, real interval enclosure row, lower and upper completion bounds, interval admission row, terminal $\RealUp$ seal, route ledger, transport, replay, provenance, and local naming rows. Equivalence of carriers is generated by the visible $\hsame$ rows and by replay of the same $\Cont$ route; it is not generated by quotient completion, chosen limits, countable-choice selectors, real trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, or selected host representatives.
\end{definition}

\begin{theorem}[Bishop interval completion NameCert obligations]
\label{thm:bishop-interval-completion-obligations}
For every accepted $\BishopIntervalCompletionUp$ carrier
$$
K=(I,S,Q,D,E,L,U,A,R,T,H,C,P,N),
$$
the local $\NameCert_{\BishopIntervalCompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source interval, stream window, regular rational readback, dyadic tolerance ledger, real interval enclosure, completion bounds, admission row, terminal real seal, route ledger, and structural rows $H,C,P,N$;
\item endpoint source discipline, requiring $I$ to provide the only rational or located interval endpoint data consumed by the packet;
\item window-readback discipline, requiring $S,Q,D$ to be read as one finite StreamName--RegSeqRat--DyadicRatCore route;
\item enclosure admission, requiring $E,L,U,A$ to bind the inspected readback and dyadic tolerance inside displayed interval bounds;
\item real-seal handoff, requiring $R$ to be reachable only after the source interval, finite window, regular readback, dyadic ledger, enclosure, bounds, and admission rows have been displayed;
\item route stability, requiring $T,H,C$ to preserve the same interval-completion route under componentwise transport and later finite-window replay;
\item exclusion, ruling out quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, and selected host representatives as local data.
\end{enumerate}
No BishopIntervalCompletion obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-interval-completion-carrier}. The projection exposes exactly the source interval row, finite stream window, regular rational readback, dyadic tolerance ledger, real interval enclosure, completion bounds, admission row, terminal real seal, route ledger, and structural rows.

The endpoint source discipline is the coordinate $I$. It is read through the rational and located interval sibling chapters before any completion-facing consumer can inspect the terminal real seal.

The finite observation face is $S,Q,D$. The stream window supplies the inspected data, the regular rational row reads that window, and the dyadic ledger supplies the tolerance scale used by the interval admission row.

The enclosure face is $E,L,U,A$. These rows place the inspected readback between displayed lower and upper completion bounds, so the packet exports an interval-completion enclosure rather than a chosen endpoint pair.

Finally $R,T,H,C,P,N$ package and replay the same route. Since no carrier coordinate contains quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, or selected host representatives, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bishop interval completion route separation]
\label{thm:bishop-interval-completion-route-separation}
Every accepted $\BishopIntervalCompletionUp$ carrier keeps the endpoint-source route and the real-seal route separated until the displayed enclosure admission row is present. In particular, a consumer may read
$$
I \longmapsto S,Q,D \longmapsto E,L,U,A
$$
as finite interval-completion evidence, but it may reach the terminal $\RealUp$ seal $R$ only through
$$
I,S,Q,D,E,L,U,A \longmapsto R \longmapsto T,H,C,P,N .
$$
Thus no Real or Completion consumer can bypass the displayed interval enclosure by using quotient completion, a selected limit, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, or a selected host representative.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(I,S,Q,D,E,L,U,A,R,T,H,C,P,N)$. The endpoint-source route begins at $I$ and reaches the finite observation rows $S,Q,D$ before any terminal real-name coordinate occurs.

The admission row $A$ is downstream of $E,L,U$. It binds the regular rational readback and dyadic tolerance to displayed interval bounds, so it is the first point where source endpoint information and finite completion evidence are jointly visible.

The real-seal row $R$ occurs only after that admission face in the carrier. Therefore a consumer seeking a terminal $\RealUp$ read must pass through the displayed source interval, finite window, regular readback, dyadic ledger, enclosure, bounds, and admission rows.

Transport and replay through $T,H,C,P,N$ preserve this order. The route ledger contains no coordinate for quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient completeness, quotient endpoint equality, or selected host representatives, so none of those routes can bypass the displayed admission row.
\end{proof}

\begin{theorem}[Bishop interval completion public route]
\label{thm:bishop-interval-completion-public-route}
The public consumer surface of an accepted $\BishopIntervalCompletionUp$ carrier is exhausted by the finite route
$$
\RationalIntervalUp,\LocatedIntervalUp \longmapsto \StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp \longmapsto \RealIntervalEnclosureUp \longmapsto \RealUp
$$
as instantiated by $I,S,Q,D,E,L,U,A,R,T,H,C,P,N$. Any downstream L10 Real and Completion argument receives only this displayed constructive interval-completion certificate and not a quotient completion, selected limit, countable-choice principle, trichotomy witness, host real equality, ambient $\RealUp$ completeness theorem, quotient endpoint equality, or host interval representative.
\end{theorem}
\begin{proof}
Read the public rows in route order. The source interval row $I$ supplies rational or located endpoint data, and the finite observation rows $S,Q,D$ turn that source into a regular rational readback with a dyadic tolerance ledger.

Next the enclosure rows $E,L,U,A$ expose the interval-completion evidence through the same finite data. A public consumer therefore receives lower and upper completion bounds only as displayed rows of the packet.

The terminal seal $R$ is then read as the $\RealUp$ handoff, with $T,H,C,P,N$ preserving the route under transport, replay, provenance, and local naming. The consumer surface is precisely the listed sibling route, so the excluded quotient, choice, trichotomy, host-equality, completeness, quotient-endpoint, and host-representative readings are outside the packet.
\end{proof}

\closureat{BishopIntervalCompletionUp}{seedStr}

\begin{closurestatus}{\BishopIntervalCompletionUp}
  \constructivestory{A $\BishopIntervalCompletionUp$ packet is generated from a rational or located interval source row, a finite StreamName window, RegSeqRat readback, DyadicRatCore tolerance ledger, RealIntervalEnclosure row, displayed completion bounds, interval admission, terminal RealUp seal, route ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-interval-completion-carrier}, \autoref{def:bishop-interval-completion-classifier}, \autoref{thm:bishop-interval-completion-obligations}, \autoref{thm:bishop-interval-completion-route-separation}, and \autoref{thm:bishop-interval-completion-public-route} seed the finite constructive interval-completion certificate over RationalInterval, LocatedInterval, StreamName, RegSeqRat, DyadicRatCore, RealIntervalEnclosure, and RealUp consumers.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.BishopIntervalCompletionUp.BishopIntervalCompletionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, quotient endpoint equality, selected host representatives, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, endpoint source discipline, StreamName--RegSeqRat--DyadicRatCore readback, enclosure admission, RealUp seal non-escape, route separation, and public-route exhaustion for BEDC.Derived.BishopIntervalCompletionUp.}
\end{closurestatus}
