\chapter{A Concrete Naming Certificate for $\UniformCauchySubsequenceUp$}
\label{ch:concrete-instances-uniform-cauchy-subsequence-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\UniformCauchySubsequenceUp$ packet records the common dyadic tail-budget subsequence interface needed on the L10 Real and Completion route. It refines the bounded subsequence route of \autoref{ch:concrete-instances-bounded-regular-cauchy-subsequence-namecert} by requiring every real-facing subsequence read to pass through one shared $\DyadicRatCoreUp$ budget row before the $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, and terminal $\RealUp$ seal are visible.

The packet is finite. It stores a bounded regular Cauchy subsequence source, displayed tail indices, a shared uniform dyadic budget row, finite observation windows, local dyadic comparisons, regular rational readback, seal routing, transport, replay, provenance, and a local certificate; it stores no selected infinite subsequence, quotient stream, countable choice, host equality, or Real completeness principle.

\begin{definition}[UniformCauchySubsequence carrier]
\label{def:uniform-cauchy-subsequence-carrier}
A $\UniformCauchySubsequenceUp$ carrier is a finite $\BHist$ packet
$$
L=(B,T,U,W,D,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the source $\BoundedRegularCauchySubsequenceUp$ row, including the bounded tail ledger, displayed monotone-cofinal schedule, and finite subsequence route already admitted by its local $\NameCert$;
\item $T$ is the exposed tail-index schedule read from $B$, with no independent choice coordinate;
\item $U$ is the shared $\DyadicRatCoreUp$ uniform tail-budget row, assigning one dyadic tolerance budget to all late windows that feed the subsequence readback;
\item $W$ records the $\StreamNameUp$ source and subsequence windows inspected under $T$ and budgeted by $U$;
\item $D$ records the local dyadic comparisons, endpoint rows, and late-window inequalities read from $U,W$;
\item $Q$ is the $\RegSeqRatUp$ readback determined by $B,T,U,W,D$;
\item $R$ records the real-facing regular subsequence handoff obtained from the same rows;
\item $E$ is the terminal $\RealUp$ seal exposed only after $Q$ and $R$ have been displayed;
\item $H$ records componentwise $\hsame$ transport for all displayed analytic and support rows;
\item $C$ records $\Cont$ replay through the route $B,T,U,W,D,Q,R,E$;
\item $P$ is the $\Pkg$ provenance over $\UniformCauchySubsequenceUp$, $\BoundedRegularCauchySubsequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\UniformCauchySubsequenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,T,U,W,D,Q,R,E,H,C,P,N$. In particular, $U$ is a named coordinate of the carrier, not a family reconstructed separately for each consumer read.
\end{definition}
\leanchecked{BEDC.Derived.UniformCauchySubsequenceUp.UniformCauchySubsequenceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Uniform tail-budget factorization]
\label{thm:uniform-cauchy-subsequence-tail-budget}
For every accepted $\UniformCauchySubsequenceUp$ carrier
$$
L=(B,T,U,W,D,Q,R,E,H,C,P,N),
$$
every $\RealUp$-facing subsequence read factors through
$$
B,T,U,W,D,Q,R,E
$$
before any seal coordinate is visible. Thus the common dyadic tail-budget row $U$ is read before the finite $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback, the regular subsequence handoff, and the terminal $\RealUp$ seal.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:uniform-cauchy-subsequence-carrier}. Its source of subsequence data is $B$, and its exposed tail schedule is $T$; neither row contains a separate selected infinite subsequence.

The next mandatory row is $U$. By definition $U$ is the shared $\DyadicRatCoreUp$ tail-budget coordinate, and the window row $W$ is admitted only as the collection of $\StreamNameUp$ windows inspected under $T$ and budgeted by $U$.

The local dyadic comparison row $D$ is downstream of $U,W$. The readback row $Q$ is then determined by $B,T,U,W,D$, and the handoff row $R$ repacks the same displayed route for the real-facing subsequence read.

Finally, the seal row $E$ is exposed only after $Q$ and $R$. The remaining rows $H,C,P,N$ transport, replay, source, and certify the displayed coordinates without adding a second route around $U$, so every visible seal read has the stated factorization.
\end{proof}

\begin{theorem}[UniformCauchySubsequence NameCert obligations]
\label{thm:uniform-cauchy-subsequence-namecert-obligations}
The local $\NameCert_{\UniformCauchySubsequenceUp}$ row is generated by exactly the following five obligation rows:
\begin{enumerate}
\item carrier admission for the finite packet $B,T,U,W,D,Q,R,E,H,C,P,N$;
\item common tail-budget stability, asserting that $\hsame$ transport preserves the shared $\DyadicRatCoreUp$ row $U$ and every late-window comparison read from it;
\item window and readback transport, carrying the $\StreamNameUp$ windows through $T,U,D$ into the $\RegSeqRatUp$ row $Q$ and the regular subsequence handoff $R$;
\item $\RealUp$-seal non-escape, asserting that no consumer reaches $E$ without passing through $B,T,U,W,D,Q,R$;
\item provenance exactness for the displayed $\Pkg$ sources $\UniformCauchySubsequenceUp$, $\BoundedRegularCauchySubsequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$.
\end{enumerate}
No additional row may name a selected infinite subsequence, quotient stream, countable choice witness, host-equality proof, or Real completeness principle.
\end{theorem}
\begin{proof}
Read the local certificate row $N$ through the classifier of \autoref{def:uniform-cauchy-subsequence-carrier}. The admissible coordinates of the carrier are precisely $B,T,U,W,D,Q,R,E,H,C,P,N$, so carrier admission is the first row and every later obligation must be a statement about these coordinates.

The common-budget row is forced by $U$. Since all window data in $W$ is budgeted by $U$, componentwise $\hsame$ transport can preserve the packet only by preserving $U$ and the dyadic comparisons recorded in $D$.

The transport and readback rows follow the displayed dependency order. Windows in $W$ are read along $T$, comparisons in $D$ are read from $U,W$, the rational readback $Q$ is determined by $B,T,U,W,D$, and $R$ is the same route repacked for the subsequence handoff.

The non-escape and provenance rows are the remaining classifier checks. The seal $E$ has no incoming coordinate except $Q,R$, while $P$ lists exactly the named sources of the packet. Therefore the five rows listed above generate the local certificate, and no excluded object has a coordinate from which a NameCert obligation could be read.
\end{proof}

\closureat{UniformCauchySubsequenceUp}{seedStr}

\begin{closurestatus}{\UniformCauchySubsequenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-subsequence-carrier}, \autoref{thm:uniform-cauchy-subsequence-tail-budget}, and \autoref{thm:uniform-cauchy-subsequence-namecert-obligations} seed the finite common tail-budget route from bounded regular Cauchy subsequence data to $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, and a $\RealUp$ seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected infinite subsequences, quotient streams, countable choice, host equality, Real completeness, Lean verification, or standard bridge checking.}
  \upgradepath{Formal closure requires checked carrier admission, common tail-budget stability, window and readback transport, Real-seal non-escape, and provenance exactness for BEDC.Derived.UniformCauchySubsequenceUp.}
  \constructivestory{A $\UniformCauchySubsequenceUp$ packet is generated from bounded regular Cauchy subsequence data, an exposed tail schedule, one shared DyadicRatCore budget row, StreamName windows, dyadic comparison rows, RegSeqRat readback, regular subsequence handoff, a RealUp seal, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
