\chapter{A Concrete Naming Certificate for $\LLPOBoundaryUp$}
\label{ch:concrete-instances-llpo-boundary-namecert}
\origin{human}

Following Brouwer and Bishop--Bridges constructive analysis, the $\LLPOBoundaryUp$ packet records the finite Real/Completion boundary at which a binary zerohood inspection may be named without importing limited principles of omniscience. It is read beside the Ishihara inspection packet of \autoref{ch:concrete-instances-ishihara-trick-namecert}, the Specker obstruction of \autoref{ch:concrete-instances-speckersequence-namecert}, the Markov boundary of \autoref{ch:concrete-instances-markov-principle-boundary-namecert}, the stream schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a positive refusal surface for later real-comparison and completion arguments: consumers may cite the displayed finite rows, but they do not receive an imported LLPO principle, an LPO test, a WLPO test, trichotomy, quotient real equality, selected limits, countable choice, or ambient $\RealUp$ completeness.

YoungIntegral-style controlled Riemann-sum consumers may read this boundary only as the finite zerohood and refusal surface used by \autoref{ch:concrete-instances-young-integral-namecert}; the read supplies no binary decision rule for choosing a hidden mesh branch.

\begin{definition}[LLPO boundary carrier]
\label{def:llpo-boundary-carrier}
An $\LLPOBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(Z_0,Z_1,S,R,D,E,W,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $Z_0$ is the left zerohood row, naming the finite stream positions whose vanishing would certify the left inspection alternative.
\item $Z_1$ is the right zerohood row, naming the finite stream positions whose vanishing would certify the right inspection alternative.
\item $S$ is the $\StreamNameUp$ schedule row listing the finite stream requests admitted by the boundary.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational values actually inspected from $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger naming the dyadic radii, endpoint comparisons, and finite margin rows used to keep the two zerohood rows apart.
\item $E$ is the $\RealUp$ seal reached only after $Z_0,Z_1,S,R,D$ have been displayed.
\item $W$ is the refusal row recording that the accepted packet exports only the displayed finite comparison data and no global LLPO decision rule.
\item $H$ stores componentwise $\hsame$ transport for the two zerohood rows, stream schedule, regular-rational readback, dyadic ledger, real seal, refusal row, continuation row, provenance row, and local name.
\item $C$ stores $\Cont$ replay from finite stream requests through $R$ and $D$, then through the zerohood rows $Z_0,Z_1$, and finally into the sealed real-facing refusal row $W$.
\item $P$ records $\Pkg$ provenance over $\LLPOBoundaryUp$, $\IshiharaTrickUp$, $\SpeckerSequenceUp$, $\MarkovPrincipleBoundaryUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LLPOBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for imported LLPO, LPO, WLPO, trichotomy, quotient real equality, countable choice, selected limits, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.LLPOBoundaryUp.LLPOBoundaryTasteGate\_single\_carrier\_alignment}

\begin{theorem}[LLPO boundary NameCert obligations]
\label{thm:llpo-boundary-namecert-obligations}
For every accepted $\LLPOBoundaryUp$ carrier $B=(Z_0,Z_1,S,R,D,E,W,H,C,P,N)$, the local $\NameCert_{\LLPOBoundaryUp}$ surface consists exactly of the following five finite obligations:
\begin{enumerate}
\item carrier exposure for the two zerohood rows, StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, refusal row, transport, continuation, package, and local naming rows;
\item classifier componentwise transport, requiring every comparison between packets to use the $\hsame$ rows stored in $H$ coordinate by coordinate;
\item zerohood separation, requiring any accepted left/right inspection to cite the displayed dyadic separation and finite margin data in $D$;
\item real-seal handoff, requiring every Real/Completion consumer to reach $E$ only after the schedule, readback, ledger, zerohood rows, and refusal row have been displayed;
\item ledger nonescape from imported LLPO, LPO, WLPO, trichotomy, quotient real equality, countable choice, selected limits, and ambient real completeness.
\end{enumerate}
No NameCert obligation is stored outside these five rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:llpo-boundary-carrier}. The visible data are the two zerohood rows $Z_0,Z_1$, the schedule $S$, readback $R$, tolerance ledger $D$, terminal seal $E$, refusal row $W$, and structural rows $H,C,P,N$.

Classifier transport is componentwise because the packet offers no aggregate classifier coordinate. A comparison of accepted packets must use the displayed $\hsame$ rows in $H$ for each zerohood row, readback, ledger, seal, refusal, replay, provenance, and local name.

Zerohood separation is forced by the tolerance ledger $D$. A consumer may inspect a left/right zerohood alternative only by naming a dyadic radius, endpoint comparison, and finite margin row already present in the ledger; otherwise $W$ records only refusal of a global binary decision rule.

The real-seal handoff is downstream of $E$, and the replay path is supplied by $C$. Since the carrier contains no coordinate for imported LLPO, LPO, WLPO, trichotomy, quotient real equality, choice, selected limits, or ambient completeness, those principles cannot be exported through the local $\NameCert_{\LLPOBoundaryUp}$ row.
\end{proof}

\begin{theorem}[LLPO boundary real-comparison refusal]
\label{thm:llpo-boundary-real-comparison-refusal}
Every Real/Completion consumer of an accepted $\LLPOBoundaryUp$ packet receives only the two displayed zerohood rows, finite schedule, regular-rational readback, dyadic ledger, terminal real seal, refusal row, componentwise transport, continuation replay, provenance, and local NameCert row. It receives no imported LLPO, no LPO, no WLPO, no trichotomy, no quotient real equality, no countable choice, no selected limit, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Let a Real/Completion consumer accept $B=(Z_0,Z_1,S,R,D,E,W,H,C,P,N)$. By \autoref{def:llpo-boundary-carrier}, the only real-facing coordinate is the seal $E$, and that seal is reached after the two zerohood rows, stream schedule, regular-rational readback, dyadic ledger, and refusal row have been displayed.

The consumer's comparison information is therefore finite. It can replay the schedule through $R$, cite only dyadic tolerance rows from $D$, and transport the two zerohood rows through $H$ and $C$.

No omitted semi-classical or completion principle is a coordinate of the packet. Thus factorization through the displayed rows cannot export imported LLPO, LPO, WLPO, trichotomy, quotient real equality, countable choice, selected limits, or ambient real completeness.
\end{proof}

\begin{theorem}[LLPO boundary Young-integral nonescape]
\label{thm:llpo-boundary-young-integral-nonescape}
Every $\YoungIntegralUp$ or controlled Riemann-sum consumer of an accepted $\LLPOBoundaryUp$ packet reads only the displayed zerohood rows $Z_0,Z_1$, stream schedule $S$, regular-rational readback $R$, dyadic tolerance ledger $D$, Real seal $E$, refusal row $W$, transport row $H$, replay row $C$, provenance row $P$, and local name $N$. It may use those rows as a finite boundary for mesh and tolerance comparisons, but it receives no imported LLPO, LPO, WLPO, trichotomy, quotient real equality, countable choice, selected limit, ambient Real completeness, or hidden branch selector.
\end{theorem}
\begin{proof}
Start with the real-comparison refusal theorem \autoref{thm:llpo-boundary-real-comparison-refusal}. It confines every Real/Completion consumer to $Z_0,Z_1,S,R,D,E,W,H,C,P,N$.

A controlled Riemann-sum consumer uses only finite comparison data. The stream schedule, regular readback, and dyadic ledger supply the same kind of finite mesh and tolerance rows that the $\YoungIntegralUp$ packet reads through its controlled-window and Riemann-sum route.

The refusal row $W$ remains part of the handoff. Since $W$ records absence of imported semi-classical decision principles, the Young-integral consumer cannot turn zerohood data into a hidden branch choice or selected refinement.

Transport, replay, provenance, and local naming preserve the same finite route. Therefore the controlled-sum consumer receives a zerohood boundary and refusal guard, not a decision principle or completion theorem.
\end{proof}

\closureat{LLPOBoundaryUp}{seedStr}

\begin{closurestatus}{\LLPOBoundaryUp}
  \constructivestory{An $\LLPOBoundaryUp$ packet is generated from two zerohood rows, a StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, refusal row, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:llpo-boundary-carrier}, \autoref{thm:llpo-boundary-namecert-obligations}, and \autoref{thm:llpo-boundary-real-comparison-refusal} seed the finite Real/Completion boundary for binary zerohood inspection.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim imported LLPO, LPO, WLPO, trichotomy, quotient real equality, countable choice, selected limits, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, classifier componentwise transport, zerohood separation, real-seal handoff, real-comparison refusal, and ledger nonescape for the same finite packet.}
\end{closurestatus}
