\chapter{A Concrete Naming Certificate for $\RealCauchyFilterUp$}
\label{ch:concrete-instances-real-cauchy-filter-namecert}
\origin{human}

Following Bourbaki and Kelley on Cauchy filters, and Bishop--Bridges on constructive real completion, the $\RealCauchyFilterUp$ packet records the finite route by which a displayed Cauchy-filter base is read as regular rational sequence data before the terminal $\RealUp$ seal is consumed. It sits after the filter-to-net correspondence of \autoref{ch:concrete-instances-cauchy-filter-net-correspondence-namecert}, the finite common-refinement operation of \autoref{ch:concrete-instances-cauchy-filter-meet-namecert}, the $\RegSeqRatUp$ handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\StreamNameUp$ window surface of \autoref{ch:concrete-instances-streamname-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal $\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite Real-facing completion interface; it is not a quotient-filter construction, ultrafilter principle, selected limit, choice principle, ambient completeness theorem, Lean verification row, or checked bridge.

\begin{definition}[Real Cauchy filter carrier]
\label{def:real-cauchy-filter-carrier}
A $\RealCauchyFilterUp$ carrier is a finite $\BHist$ packet
$$
R=(F,M,D,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the filter-base row. It records the finite Cauchy-filter base requests, refinement witnesses, and membership reads available before any real-facing consumer inspects the packet.
\item $M$ is the finite meet row. It records the $\CauchyFilterMeetUp$ common-refinement reads that combine two displayed base requests over the same Cauchy-filter surface.
\item $D$ is the dyadic entourage and tolerance ledger. It records the requested dyadic scale, the refinement scale used by the meet row, and the comparison showing that the displayed base request is Cauchy at that scale.
\item $S$ is the regular-sequence extraction row. It reads finite windows through $\StreamNameUp$ and repacks the accepted Cauchy-filter observations as $\RegSeqRatUp$ data.
\item $Q$ is the terminal $\RealUp$ seal row reached only after $F,M,D,S$ have been displayed.
\item $E$ records the $\hsame$ transport routes for the filter base, meet, dyadic ledger, regular-sequence extraction, Real seal, continuation, provenance, and local naming rows.
\item $H$ records displayed $\Cont$ replay from a Real-facing precision request through $F,M,D,S,Q$ in that order.
\item $C$ is the $\Pkg$ provenance over $\RealCauchyFilterUp$, $\CauchyFilterNetCorrespondenceUp$, $\CauchyFilterMeetUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $P$ records the local package provenance tying the displayed route to the surrounding Real-and-Completion corridor.
\item $N$ is the local $\NameCert_{\RealCauchyFilterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed route
$$
F,M,D,S,Q \longmapsto E,H,C,P,N .
$$
There is no carrier coordinate for quotient filters, ultrafilters, selected limits, Classical.choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Real Cauchy filter NameCert obligations]
\label{thm:real-cauchy-filter-namecert-obligations}
For every accepted $\RealCauchyFilterUp$ carrier
$$
R=(F,M,D,S,Q,E,H,C,P,N),
$$
the local $\NameCert_{\RealCauchyFilterUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the filter-base row, finite meet row, dyadic tolerance ledger, regular-sequence extraction row, terminal Real seal, transport, replay, provenance, and local naming row;
\item filter-base stability, requiring every transported base request to remain within the displayed $\hsame$ route before any meet or extraction row is read;
\item finite-meet closure, requiring pairs of displayed base requests to pass through $M$ and return a common refinement over the same filter-base row;
\item Cauchy entailment, requiring each Real-facing tolerance request to be witnessed by the dyadic ledger $D$ after the finite meet row has been read;
\item regular-sequence handoff, requiring the accepted filter observations to pass through $\StreamNameUp$ windows and the $\RegSeqRatUp$ extraction row $S$ before the Real seal is visible;
\item $\RealUp$ seal descent, requiring the terminal row $Q$ to be consumed only after the route $F,M,D,S$ has been replayed;
\item nonescape, requiring the provenance and local naming rows to export no quotient filters, ultrafilters, selected limits, Classical.choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-cauchy-filter-carrier}. The projection exposes exactly the filter base, finite meet, dyadic tolerance ledger, regular-sequence extraction, Real seal, transport, replay, provenance, and local naming rows.

Filter-base stability is supplied by the $\hsame$ row $E$. A transported precision request must still name the same displayed base surface before it can be routed to $M$, $D$, or $S$.

Finite-meet closure is the role of $M$. Given two displayed base requests, the meet row names a common finite refinement over the same filter base; it does not appeal to an ambient lattice of filters or to quotient-filter equality.

Cauchy entailment is read through $D$. After the meet row has fixed a common refinement, the dyadic ledger records the requested tolerance and the smaller displayed tolerance that makes the base request Cauchy at the requested scale.

The regular-sequence handoff then passes through $S$. This row reads the same observations through $\StreamNameUp$ windows and repacks them as $\RegSeqRatUp$ data before the terminal seal can be consumed.

Finally the Real seal row $Q$ is downstream of the whole route, while $H,C,P,N$ only replay, source, and name that route. The excluded quotient, ultrafilter, selected-limit, choice, ambient-completeness, verification, and bridge-checking data therefore remain outside the local NameCert surface.
\end{proof}

\begin{theorem}[Real Cauchy filter regular-sequence handoff]
\label{thm:real-cauchy-filter-regular-sequence-handoff}
Every $\RealUp$-facing read exported by an accepted $\RealCauchyFilterUp$ carrier
$$
R=(F,M,D,S,Q,E,H,C,P,N)
$$
factors through the finite route
$$
F \longmapsto M \longmapsto D \longmapsto S \longmapsto Q \longmapsto E,H,C,P,N .
$$
In particular, the read first consumes the filter-base row, then the finite-meet row, then the dyadic tolerance ledger, then the $\StreamNameUp$ and $\RegSeqRatUp$ extraction row, and only then the terminal $\RealUp$ seal. It receives no quotient filter, ultrafilter, selected limit, Classical.choice, ambient completeness principle, Lean verification row, or bridge certificate.
\end{theorem}
\begin{proof}
Begin with a Real-facing consumer named by the provenance rows. By \autoref{def:real-cauchy-filter-carrier}, the only terminal Real coordinate is $Q$, and the displayed continuation to $Q$ is routed through $F,M,D,S$.

The filter-base row $F$ supplies the source requests. The finite meet row $M$ then aligns pairs of such requests into common refinements over the same base, so the route has no need for quotient filters or ultrafilters.

The dyadic ledger $D$ records the tolerance comparison attached to the chosen refinement. This is the Cauchy evidence consumed by the later regular-sequence extraction row, not a selected host limit.

Next $S$ reads the displayed observations through $\StreamNameUp$ windows and repacks the route as $\RegSeqRatUp$ data. Only after that handoff can the terminal $\RealUp$ seal row $Q$ be inspected.

The structural rows $E,H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier inventory has no coordinate for quotient filters, ultrafilters, selected limits, Classical.choice, ambient completeness, Lean verification, or bridge checking, every Real-facing read is exhausted by the factorization above.
\end{proof}

\begin{closurestatus}{\RealCauchyFilterUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-cauchy-filter-carrier}, \autoref{thm:real-cauchy-filter-namecert-obligations}, and \autoref{thm:real-cauchy-filter-regular-sequence-handoff} seed the finite Cauchy-filter route into regular rational sequence data and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, ultrafilters, selected limits, Classical.choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, filter-base stability, finite-meet closure, Cauchy entailment, regular-sequence handoff, RealUp seal descent, transport, replay, provenance, and local naming for BEDC.Derived.RealCauchyFilterUp.}
  \constructivestory{A $\RealCauchyFilterUp$ packet is generated from a filter-base row, finite meet row, dyadic tolerance ledger, regular-sequence extraction row, Real seal row, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
