\chapter{A Concrete Naming Certificate for $\LocatedRealNestedIntervalsUp$}
\label{ch:concrete-instances-located-real-nested-intervals-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedRealNestedIntervalsUp$ packet records the finite located nested-interval bridge from displayed interval bisections to regular Cauchy real names. It consumes the located endpoint-plus-radius surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, the branch route of \autoref{ch:concrete-instances-located-interval-bisection-namecert}, the midpoint handoff of \autoref{ch:concrete-instances-located-interval-midpoint-namecert}, the retained-window discipline of \autoref{ch:concrete-instances-nestedinterval-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite BEDC route for nested located intervals; it is not a host interval-intersection theorem, a selected quotient representative, open-cover compactness, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Located real nested intervals carrier]
\label{def:located-real-nested-intervals-carrier}
A $\LocatedRealNestedIntervalsUp$ carrier is a finite $\BHist$ packet
$$
Z=(I,B,M,D,J,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the source $\LocatedRealIntervalUp$ row, including endpoint names, radius data, locator reads, locatedness modulus, and metric bracket rows.
\item $B$ is the $\LocatedIntervalBisectionUp$ row that records the finite retained branch route from the source interval.
\item $M$ is the $\LocatedIntervalMidpointUp$ row that supplies the midpoint and child-cell handoff used by each retained branch.
\item $D$ is the diameter-budget row. It records the finite dyadic contraction schedule, the positive tolerance requests, and the proof rows that each retained child interval has a smaller displayed diameter than its predecessor.
\item $J$ is the nested-containment row. It records that the retained located intervals are nested through displayed endpoint, midpoint, and branch witnesses rather than through a host intersection object.
\item $S$ is the $\StreamNameUp$ finite-window row obtained from the retained lower and upper endpoint windows at the requested precisions.
\item $R$ is the $\RegSeqRatUp$ readback row for the same retained windows and diameter budgets.
\item $E$ is the terminal $\RealUp$ seal reached only after $D,J,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the located interval rows, bisection rows, midpoint rows, diameter budgets, containment witnesses, stream windows, regular readbacks, real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a nested-interval or point-name request through $I,B,M,D,J,S,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedRealNestedIntervalsUp$, $\LocatedRealIntervalUp$, $\LocatedIntervalBisectionUp$, $\LocatedIntervalMidpointUp$, $\NestedIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedRealNestedIntervalsUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite located nested-interval history. It has no coordinate for host interval intersection, selected quotient representatives, open-cover compactness, countable choice, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.LocatedRealNestedIntervalsUp.LocatedRealNestedIntervalsTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Located real nested intervals diameter contraction]
\label{thm:located-real-nested-intervals-diameter-contracts}
For every accepted $\LocatedRealNestedIntervalsUp$ carrier $Z=(I,B,M,D,J,S,R,E,H,C,P,N)$, every retained interval row exposed by $J$ is downstream of the diameter-budget row $D$. In particular, any finite precision request reaching the stream-window row $S$ first reads a displayed contraction witness in $D$, then the nested containment witness in $J$, and only then the retained endpoint windows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-real-nested-intervals-carrier}. The projection exposes the source located interval, the finite bisection route, midpoint handoffs, diameter budgets, containment witnesses, stream windows, regular readback, and structural rows.

The contraction data are stored in $D$. Each requested precision has a displayed dyadic tolerance budget and a retained-child diameter row, so a consumer cannot inspect a retained window before the corresponding budget has been read.

The containment data are stored in $J$. Its rows bind each retained located interval to the previous one through the endpoint, midpoint, and branch witnesses supplied by $I,B,M,D$.

Finally $S$ is downstream of $D$ and $J$. The finite stream windows are therefore exposed only after the contraction and containment rows have fixed the retained interval route, and no host intersection or compactness coordinate is available from the carrier.
\end{proof}

\begin{theorem}[Located real nested intervals point-name route]
\label{thm:located-real-nested-intervals-point-name}
Every $\RealUp$-facing point-name read of an accepted $\LocatedRealNestedIntervalsUp$ carrier factors through the finite route
$$
I \longmapsto B,M \longmapsto D,J \longmapsto S,R \longmapsto E,H,C,P,N .
$$
Thus the read first consumes the located interval source, then the finite bisection and midpoint rows, then the diameter-contraction and nested-containment rows, then the $\StreamNameUp$ windows and $\RegSeqRatUp$ readback, and only then the terminal $\RealUp$ seal. The route exports no host interval intersection, selected quotient representative, open-cover compactness, countable-choice schedule, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with an accepted packet $Z=(I,B,M,D,J,S,R,E,H,C,P,N)$. The only source interval coordinate is $I$, so endpoint, radius, locator, and locatedness observations begin at the displayed $\LocatedRealIntervalUp$ row.

The next stage is $B,M$. The bisection row records the retained finite branch route, while the midpoint row supplies the child-cell handoff for each retained branch.

The diameter and containment stage is $D,J$. These rows state that the retained intervals contract at the requested precisions and that each retained row is nested inside the previous displayed row.

The readback stage is $S,R$. The stream windows are taken from the retained endpoint windows fixed by $D,J$, and the regular rational row repacks exactly those windows as the point-name readback.

Finally the seal stage is $E,H,C,P,N$. The $\RealUp$ seal is reached only after the regular readback, and the structural rows transport, replay, package, and name the same finite route. Since the carrier has no host intersection, quotient-representative selector, compactness, choice, or completeness coordinate, the displayed route is exhaustive.
\end{proof}

\begin{definition}[Located real nested intervals classifier]
\label{def:located-real-nested-intervals-classifier}
For an accepted $\LocatedRealNestedIntervalsUp$ carrier $Z=(I,B,M,D,J,S,R,E,H,C,P,N)$, the local classifier is the finite predicate that admits exactly the reads transported through the following rows:
\begin{enumerate}
\item the source transported located interval row $I$;
\item the bisection branch row $B$ and midpoint row $M$;
\item the diameter-budget row $D$ and nested-containment row $J$;
\item the $\StreamNameUp$ row $S$ and $\RegSeqRatUp$ readback row $R$;
\item the terminal $\RealUp$ seal $E$;
\item the transport, replay, provenance, and local naming rows $H,C,P,N$.
\end{enumerate}
The classifier rejects every read that bypasses one of these rows or asks for a host interval intersection, a selected quotient representative, open-cover compactness, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located real nested intervals NameCert obligations]
\label{thm:located-real-nested-intervals-namecert-obligations}
For every accepted $\LocatedRealNestedIntervalsUp$ carrier $Z=(I,B,M,D,J,S,R,E,H,C,P,N)$, the local $\NameCert_{\LocatedRealNestedIntervalsUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the located interval row, bisection row, midpoint row, diameter budget, containment row, stream windows, regular readback, Real seal, transport, replay, provenance, and local naming;
\item classifier stability under componentwise $\hsame$ transport of $I,B,M,D,J,S,R,E$;
\item diameter contraction for every retained interval row exposed by $J$;
\item nested containment from the source located interval through the retained branch and midpoint rows;
\item $\StreamNameUp$ window exposure using only the retained endpoint windows fixed by $D,J$;
\item $\RegSeqRatUp$ readback from the same retained windows;
\item $\RealUp$ seal nonescape through $S,R,E$;
\item displayed $\Cont$ replay and $\Pkg$ provenance for the whole route;
\item ledger refusal for any consumer that omits a located interval row, bisection row, midpoint row, diameter budget, containment row, stream window, regular readback, Real seal, transport row, replay row, provenance row, or local naming row.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-real-nested-intervals-carrier}. This gives the displayed rows $I,B,M,D,J,S,R,E,H,C,P,N$ and no additional host-level intersection, quotient, compactness, choice, or completeness coordinate.

The classifier is stable because \autoref{def:located-real-nested-intervals-classifier} is defined rowwise from the transported located interval, bisection, midpoint, diameter, containment, stream, readback, and seal rows. Componentwise $\hsame$ transport therefore preserves exactly the admitted reads.

The diameter and containment obligations are the two gates of \autoref{thm:located-real-nested-intervals-diameter-contracts}. Every retained interval window downstream of $J$ first reads the budget row $D$, then the containment row $J$.

The readback and seal obligations are chained through \autoref{thm:located-real-nested-intervals-point-name}. The route reaches $S,R$ only after $D,J$, and it reaches $E$ only after the StreamName and RegSeqRat rows have been displayed.

Finally $H,C,P,N$ transport, replay, package, and name the same finite route. Any consumer missing one of the listed rows fails the local classifier and is refused by the NameCert ledger.
\end{proof}

\begin{theorem}[Located real nested intervals Real seal nonescape]
\label{thm:located-real-nested-intervals-real-seal-nonescape}
Every $\RealUp$-facing read accepted by the $\LocatedRealNestedIntervalsUp$ classifier passes through
$$
I,B,M,D,J,S,R,E,H,C,P,N .
$$
In particular, no accepted read reaches the terminal $\RealUp$ seal from a host interval-intersection object, a selected quotient representative, an open-cover compactness proof, a countable-choice schedule, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Let a read be accepted by the classifier of \autoref{def:located-real-nested-intervals-classifier}. By definition, the read is classified only when it is transported through the source located interval, bisection, midpoint, diameter-budget, containment, stream-window, regular-readback, Real-seal, transport, replay, provenance, and local naming rows.

Apply \autoref{thm:located-real-nested-intervals-diameter-contracts} to the retained interval stage. The read cannot reach $S$ before the contraction row $D$ and containment row $J$ have been displayed.

Apply \autoref{thm:located-real-nested-intervals-point-name} to the terminal route. The read reaches $E$ only after $I,B,M,D,J,S,R$ and remains packaged by $H,C,P,N$.

The carrier of \autoref{def:located-real-nested-intervals-carrier} contains no alternate coordinate for host intersection, quotient selection, compactness, choice, or completeness. Hence every accepted $\RealUp$-facing read is forced through the displayed finite route.
\end{proof}

\closureat{LocatedRealNestedIntervalsUp}{seedStr}

\begin{closurestatus}{\LocatedRealNestedIntervalsUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-real-nested-intervals-carrier}, \autoref{thm:located-real-nested-intervals-diameter-contracts}, and \autoref{thm:located-real-nested-intervals-point-name} seed the finite located nested-interval bridge from located interval bisection and midpoint rows to StreamName, RegSeqRat, and Real seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host interval intersection, selected quotient representatives, open-cover compactness, countable choice, ambient $\RealUp$ completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, diameter contraction, nested containment, StreamName window exposure, RegSeqRat readback, Real seal nonescape, and point-name route proofs for BEDC.Derived.LocatedRealNestedIntervalsUp.}
  \constructivestory{A $\LocatedRealNestedIntervalsUp$ packet is generated from a source LocatedRealIntervalUp row, LocatedIntervalBisectionUp branch rows, LocatedIntervalMidpointUp child-cell rows, dyadic diameter budgets, nested containment witnesses, StreamNameUp windows, RegSeqRatUp readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
