\chapter{A Concrete Naming Certificate for $\DyadicMetricUp$}
\label{ch:concrete-instances-dyadic-metric-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DyadicMetricUp$ packet names the finite dyadic metric ledger read by regular rational streams, real-name seals, and metric-space consumers before any ambient completion can be invoked. It sits over the dyadic endpoint and distance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, reads the nonnegative endpoint surface of \autoref{ch:concrete-instances-dyadicabsolutevalue-namecert}, hands scheduled distance ledgers to \autoref{ch:concrete-instances-regseqrat-namecert}, and presents the resulting finite witness surface to \autoref{ch:concrete-instances-metric-namecert}. The chapter isolates the metric ledger itself: source pairs, dyadic distance, zero boundary, symmetry, triangle bounds, consumer handoff, transport, replay, provenance, and local naming.

\begin{definition}[Dyadic metric carrier]
\label{def:dyadic-metric-carrier}
A $\DyadicMetricUp$ carrier is a finite $\BHist$ packet
$$
M=(s,d,a,z,u,t,r,h,c,p,n)
$$
with the following displayed rows:
\begin{enumerate}
\item $s$ is the source-pair row. It records two accepted $\DyadicRatCoreUp$ endpoints together with their visible mantissa, denominator, $\IntUp$, and $\RatUp$ provenance.
\item $d$ is the dyadic distance ledger for the ordered pair in $s$. It records the common-denominator subtraction window, radius row, and finite comparison data used by distance consumers.
\item $a$ is the $\DyadicAbsoluteValueUp$ endpoint row attached to $d$, exposing the nonnegative dyadic distance endpoint through the absolute-value packet rather than through a host absolute-value function.
\item $z$ is the zero-distance boundary row. It states that a displayed zero distance is admitted only by the finite dyadic equality boundary already visible in the source-pair and distance rows.
\item $u$ is the symmetry row. It swaps the two source endpoints and reuses the same absolute-value endpoint and tolerance ledger with the ordered-pair direction reversed.
\item $t$ is the triangle-bound row. It records the finite three-source ledger, the two intermediate distance rows, the outer distance row, and the dyadic comparison witnessing the displayed triangle bound.
\item $r$ is the $\RegSeqRatUp$ and $\RealUp$ consumer handoff row. It exposes the distance ledger as the finite tolerance surface read by regular rational streams, real-name seals, and metric witnesses.
\item $h$ records componentwise $\hsame$ transport for the source pair, dyadic distance ledger, absolute-value endpoint, zero boundary, symmetry row, triangle-bound row, consumer handoff, replay, provenance, and local naming rows.
\item $c$ records displayed $\Cont$ replay from the source pair through dyadic distance, absolute value, zero boundary, symmetry, triangle bound, consumer handoff, transport, provenance, and local naming.
\item $p$ is the $\Pkg$ provenance over $\DyadicMetricUp$, $\DyadicRatCoreUp$, $\DyadicAbsoluteValueUp$, $\RegSeqRatUp$, $\RealUp$, $\MetricSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $n$ is the local $\NameCert_{\DyadicMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $s,d,a,z,u,t,r,h,c,p,n$. It has no coordinate for host metric spaces, quotient rationals, trichotomy, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Dyadic metric NameCert obligations]
\label{thm:dyadic-metric-namecert-obligations}
For every accepted $\DyadicMetricUp$ carrier $M=(s,d,a,z,u,t,r,h,c,p,n)$, the local $\NameCert_{\DyadicMetricUp}$ surface consists exactly of carrier admission, dyadic distance-ledger exposure, absolute-value endpoint exposure, zero-distance boundary, symmetry routing, triangle-bound routing, RegSeqRat and Real consumer handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row. No dyadic metric obligation is stored outside those finite rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dyadic-metric-carrier}. The visible packet lists the source pair $s$, dyadic distance ledger $d$, absolute-value endpoint $a$, zero boundary $z$, symmetry row $u$, triangle-bound row $t$, consumer handoff $r$, and structural rows $h,c,p,n$.

The metric-law rows are finite ledger rows, not external laws. The zero boundary reads only the displayed dyadic equality boundary; the symmetry row swaps the source pair and reuses the same absolute-value endpoint; the triangle row reads three displayed sources, the corresponding distance ledgers, and one dyadic comparison row.

The handoff clause is downstream of those ledgers. A $\RegSeqRatUp$, $\RealUp$, or $\MetricSpaceUp$ consumer can read the distance only through $r$ after the source pair, distance ledger, absolute-value endpoint, and metric-law rows have already been displayed.

Transport and replay are componentwise through $h$ and $c$. The provenance and local naming rows package exactly the listed coordinates, so the excluded host metric, quotient-rational, trichotomy, selected-limit, completeness, verification, and bridge data cannot appear as hidden obligations.
\end{proof}

\begin{theorem}[Dyadic metric RegSeqRat consumer handoff]
\label{thm:dyadic-metric-regseqrat-consumer-handoff}
Let $M=(s,d,a,z,u,t,r,h,c,p,n)$ be an accepted $\DyadicMetricUp$ carrier. Every $\RegSeqRatUp$, $\RealUp$, or $\MetricSpaceUp$ consumer of $M$ must read the finite route
$$
s \longmapsto d \longmapsto a \longmapsto z,u,t \longmapsto r \longmapsto h,c,p,n
$$
before the dyadic distance ledger is available as a regular-rational tolerance, a real-name distance surface, or a metric witness. Consequently the consumer route cannot bypass the dyadic metric packet through a host metric space, quotient rational equality, trichotomy, selected limit, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only consumer-facing coordinate is $r$, and $r$ is placed after the source-pair row, dyadic distance ledger, absolute-value endpoint, zero boundary, symmetry row, and triangle-bound row.

For a $\RegSeqRatUp$ consumer, the distance ledger is read as a dyadic tolerance row. Since the tolerance comes from $d$ and $a$, the regular rational route must pass through the displayed source pair and nonnegative endpoint before it can inspect a scheduled finite window.

For a $\RealUp$ or $\MetricSpaceUp$ consumer, the same route is terminal. The real-name seal and the metric witness receive only the distance surface exposed by $r$, while $h,c,p,n$ transport, replay, package, and name that surface without adding a second distance function.

The excluded objects are absent from the carrier. Thus every accepted consumer route factors through the displayed dyadic metric ledger and cannot obtain an ambient host metric, quotient-rational comparison, trichotomy witness, selected limit, or completeness theorem from this packet.
\end{proof}

\closureat{DyadicMetricUp}{seedStr}

\begin{closurestatus}{\DyadicMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-metric-carrier}, \autoref{thm:dyadic-metric-namecert-obligations}, and \autoref{thm:dyadic-metric-regseqrat-consumer-handoff} seed the finite dyadic metric route from source pairs through distance ledger, absolute-value endpoint, zero boundary, symmetry, triangle bound, RegSeqRat and Real handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host metric spaces, quotient rationals, trichotomy, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic distance-ledger exposure, absolute-value endpoint exposure, zero-distance boundary, symmetry routing, triangle-bound routing, consumer handoff, provenance, transport, replay, and local naming for BEDC.Derived.DyadicMetricUp.}
  \constructivestory{A $\DyadicMetricUp$ packet is generated from a displayed pair of DyadicRatCore endpoints, a dyadic distance ledger, a DyadicAbsoluteValue endpoint, zero-distance, symmetry, and triangle rows, a RegSeqRat and Real consumer handoff, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
