\chapter{A Concrete Naming Certificate for $\MonotoneSubsequenceTheoremUp$}
\label{ch:concrete-instances-monotone-subsequence-theorem-namecert}
\origin{human}

Following Erd\H{o}s--Szekeres and Bishop--Bridges constructive analysis, the $\MonotoneSubsequenceTheoremUp$ packet records the finite selector-theorem surface used by downstream compactness routes. It stores source sequence windows, a peak-valley or monotone-branch selector ledger, cofinality rows, selected monotone windows, dyadic tolerance rows, a $\RegSeqRatUp$ handoff, a $\RealUp$ seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ data. It is a displayed certificate surface for finite BEDC consumers, not a countable-choice principle or an open-cover compactness theorem.

\begin{definition}[Monotone subsequence theorem carrier]
\label{def:monotone-subsequence-theorem-carrier}
A $\MonotoneSubsequenceTheoremUp$ carrier is a finite $\BHist$ packet
$$
T=(S,B,Q,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source sequence-window ledger. Each row records the inspected finite source window and the comparison cells visible to the theorem surface.
\item $B$ is the peak-valley or monotone-branch selector ledger. A row either records a displayed peak-valley split or records the finite monotone branch selected from the inspected window.
\item $Q$ is the cofinality evidence for the inspected selector thresholds, limited to the thresholds that occur in the packet.
\item $W$ is the selected monotone-window family read from $S,B,Q$ through the finite $\MonotoneSubsequenceUp$ route of \autoref{ch:concrete-instances-monotone-subsequence-namecert}.
\item $D$ is the dyadic tolerance ledger attached to the selected windows before any regular-rational or real-facing handoff is available.
\item $R$ is the $\RegSeqRatUp$ handoff row for the selected monotone windows.
\item $E$ is the $\RealUp$ seal row exposed only after the selected-window handoff has passed through $D$ and $R$.
\item $H$ stores componentwise $\hsame$ transport for source windows, branch rows, cofinality rows, selected monotone windows, dyadic tolerance rows, the regular handoff, the Real seal, continuation rows, provenance rows, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from $S,B,Q$ to $W$, from $W$ to $D$, from $D$ to $R$, and from $R$ to $E$.
\item $P$ is the $\Pkg$ provenance over $\MonotoneSubsequenceTheoremUp$, $\MonotoneSubsequenceUp$, $\BolzanoWeierstrassSelectorUp$, $\BolzanoWeierstrassUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MonotoneSubsequenceTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these eleven rows. It has no coordinate for countable choice, arbitrary infinite subsequence selection, quotient stream equality, host real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.MonotoneSubsequenceTheoremUp.TasteGate.MonotoneSubsequenceTheoremTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Monotone subsequence theorem NameCert obligations]
\label{thm:monotone-subsequence-theorem-namecert-obligations}
For every accepted $\MonotoneSubsequenceTheoremUp$ carrier
$$
T=(S,B,Q,W,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\MonotoneSubsequenceTheoremUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed source windows, branch ledger, cofinality rows, selected monotone windows, dyadic rows, regular handoff, seal row, transport, replay, provenance, and local name;
\item branch stability for the peak-valley or monotone-branch selector ledger under the recorded $\hsame$ transports;
\item cofinal coverage for every inspected selector threshold listed in $Q$;
\item selected-window handoff through $\StreamNameUp$ and $\RegSeqRatUp$ before the $\RealUp$ seal row is consumed;
\item non-escape from countable choice, arbitrary infinite subsequence selection, quotient stream equality, host real equality, open-cover compactness, and ambient $\RealUp$ completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:monotone-subsequence-theorem-carrier}. The rows $S,B,Q,W,D,R,E,H,C,P,N$ are the only available coordinates, so carrier admission is exactly admission of those displayed rows.

The selector-theorem content is finite. Branch stability is read from the peak-valley or monotone-branch ledger $B$, and cofinal coverage is read from the inspected-threshold ledger $Q$. The actual selected windows then route through the finite $\MonotoneSubsequenceUp$ packet of \autoref{ch:concrete-instances-monotone-subsequence-namecert}.

The analytic handoff uses the existing downstream interfaces. Selected windows are consumed through the $\StreamNameUp$ surface of \autoref{ch:concrete-instances-streamname-namecert}, dyadic tolerance rows feed the $\RegSeqRatUp$ handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and only then does the terminal $\RealUp$ boundary of \autoref{ch:concrete-instances-real-namecert} become visible.

Finally inspect the excluded data. The carrier has no row for countable choice, arbitrary infinite subsequence selection, quotient stream equality, host real equality, open-cover compactness, or ambient completeness, and the structural rows only transport, replay, source, and name the displayed packet. Hence the five listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Monotone subsequence theorem Bolzano--Weierstrass handoff]
\label{thm:monotone-subsequence-theorem-bolzano-weierstrass-handoff}
Every accepted $\MonotoneSubsequenceTheoremUp$ packet exports to Bolzano--Weierstrass consumers only the finite route
$$
S,B,Q\longmapsto W\longmapsto D\longmapsto R\longmapsto E.
$$
The handoff factors through \autoref{ch:concrete-instances-monotone-subsequence-namecert}, \autoref{ch:concrete-instances-bolzanoweierstrassselector-namecert}, and \autoref{ch:concrete-instances-bolzanoweierstrass-namecert}; its window, regular-rational, and Real endpoints are read through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\begin{proof}
Start with the selector route. The source windows $S$, branch ledger $B$, and inspected cofinality rows $Q$ determine the selected monotone windows $W$ only through the finite selector packet recorded in \autoref{ch:concrete-instances-monotone-subsequence-namecert}.

Next pass to the Bolzano--Weierstrass selector boundary. The selector consumer of \autoref{ch:concrete-instances-bolzanoweierstrassselector-namecert} receives the selected monotone windows together with their dyadic tolerance and regular handoff rows, not an ambient subsequence object.

The Bolzano--Weierstrass chapter of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert} can therefore consume only the displayed route. The windows are read through \autoref{ch:concrete-instances-streamname-namecert}, the selected regular-rational handoff is read through \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal is read through \autoref{ch:concrete-instances-real-namecert}.

Since the route has no row for countable choice, arbitrary infinite subsequence selection, quotient stream equality, host real equality, open-cover compactness, or ambient $\RealUp$ completeness, every Bolzano--Weierstrass-facing use remains inside the finite selector-certificate surface.
\end{proof}

\closureat{MonotoneSubsequenceTheoremUp}{seedStr}

\begin{closurestatus}{\MonotoneSubsequenceTheoremUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:monotone-subsequence-theorem-carrier}, \autoref{thm:monotone-subsequence-theorem-namecert-obligations}, and \autoref{thm:monotone-subsequence-theorem-bolzano-weierstrass-handoff} seed the finite selector-theorem carrier, its local NameCert obligations, and its Bolzano--Weierstrass handoff boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim countable choice, arbitrary infinite subsequence selection, quotient stream equality, host real equality, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, branch stability, inspected-threshold cofinal coverage, selected-window RegSeqRat handoff, and Bolzano--Weierstrass handoff non-escape for BEDC.Derived.MonotoneSubsequenceTheoremUp.}
  \constructivestory{A $\MonotoneSubsequenceTheoremUp$ packet is generated from source sequence windows, a peak-valley or monotone-branch selector ledger, cofinality rows, selected monotone windows, dyadic tolerance rows, a RegSeqRat handoff, a RealUp seal, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
\end{closurestatus}
