\chapter{A Concrete Naming Certificate for $\RegularCauchyMaximumUp$}
\label{ch:concrete-instances-regular-cauchy-maximum-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyMaximumUp$ packet records the constructive upper member of two regular rational Cauchy real names by reducing the public route to already displayed regular Cauchy arithmetic. It reads the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic arithmetic surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the absolute-value lift of \autoref{ch:concrete-instances-regularcauchyabs-namecert}, the addition surface of \autoref{ch:concrete-instances-regularcauchysum-namecert}, the subtraction surface of \autoref{ch:concrete-instances-regularcauchydifference-namecert}, the sibling lower-bound packet of \autoref{ch:concrete-instances-regular-cauchy-minimum-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The certificate gives downstream $\RealUp$ consumers a finite maximum route without assuming quotient streams, selected limits, trichotomy, countable choice, or ambient completeness.

\begin{definition}[Regular Cauchy maximum carrier]\label{def:regular-cauchy-maximum-carrier}
A $\RegularCauchyMaximumUp$ carrier is a finite $\BHist$ packet
$$
M=(X,Y,W_X,W_Y,D,S,A,U,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two accepted $\RealUp$ rows presented by regular Cauchy names; each exposes only its finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, dyadic tolerance ledger, and terminal real seal.
\item $W_X$ and $W_Y$ are aligned finite observation windows for the two names at the requested output tolerance.
\item $D$ is the $\DyadicRatCoreUp$ subtraction ledger for the displayed difference $X-Y$ read through $W_X$ and $W_Y$.
\item $S$ is the $\RegularCauchyDifferenceUp$ row repacking the pointwise dyadic subtraction route as a regular Cauchy difference name.
\item $A$ is the $\RegularCauchyAbsUp$ row applied to the displayed difference route $S$.
\item $U$ is the $\RegularCauchySumUp$ row adding the two source names and the absolute-difference row on the shared observation scale.
\item $R$ is the final regular Cauchy readback row for the half-sum maximum route, with the dyadic division-by-two ledger displayed inside the same finite tolerance budget.
\item $E$ is the $\RealUp$ seal row reached only after $R$ has been exposed.
\item $H$ records componentwise $\hsame$ transport for the two inputs, windows, dyadic subtraction, difference row, absolute-difference row, sum row, half-sum readback, real seal, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from a maximum request through $X,Y,W_X,W_Y,D,S,A,U,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyMaximumUp$, $\RegularCauchyMinimumUp$, $\RegularCauchyAbsUp$, $\RegularCauchySumUp$, $\RegularCauchyDifferenceUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyMaximumUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,W_X,W_Y,D,S,A,U,R,E,H,C,P,N$. The carrier has no coordinate for a host maximum function, trichotomy, quotient stream equality, selected limit, countable-choice schedule, ambient $\RealUp$ completeness principle, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyMaximumUp.RegularCauchyMaximumTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy maximum NameCert obligations]\label{thm:regular-cauchy-maximum-namecert-obligations}
For every accepted $\RegularCauchyMaximumUp$ carrier
$$
M=(X,Y,W_X,W_Y,D,S,A,U,R,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyMaximumUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission for the two regular Cauchy real rows, aligned stream windows, dyadic subtraction ledger, difference row, absolute-difference row, sum row, half-sum readback, real seal, transport, replay, provenance, and local name;
\item aligned-window exposure, requiring every output request to display matching $\StreamNameUp$ windows for $X$ and $Y$ before any dyadic subtraction, absolute value, sum, or seal row is consumed;
\item arithmetic route exactness, requiring $D,S,A,U,R$ to be read in the order subtraction, regular Cauchy difference, regular Cauchy absolute value, regular Cauchy sum, and dyadic half-sum readback;
\item classifier stability, requiring componentwise $\hsame$ transport of $X,Y,W_X,W_Y,D,S,A,U,R,E,C,P,N$ to preserve the accepted maximum route;
\item non-escape, requiring $H,C,P,N$ to transport, replay, source, and name no host maximum, trichotomy, quotient stream equality, selected limit, countable choice, ambient Real completeness, Lean verification, or bridge credential.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-maximum-carrier}. Its displayed rows are exactly the two regular Cauchy real inputs, aligned stream windows, dyadic subtraction ledger, regular Cauchy difference row, absolute-difference row, sum row, half-sum readback, real seal, and structural rows.

Aligned-window exposure follows because $D$ has no independent source coordinate. The subtraction ledger can read endpoints only through $W_X$ and $W_Y$, so the later rows $S,A,U,R,E$ remain downstream of the displayed finite windows.

Arithmetic route exactness is ledger order. The difference row $S$ consumes $D$, the absolute-difference row $A$ consumes $S$, the sum row $U$ consumes $X,Y,A$, and the readback row $R$ records the dyadic division by two before $E$ seals the result as a real name.

Classifier stability and non-escape are coordinate exhaustion. The only permitted transports and replays are $H$ and $C$, and the provenance and naming rows $P,N$ cite no excluded host or quotient object.
\end{proof}

\begin{theorem}[Regular Cauchy maximum abs-sum route]\label{thm:regular-cauchy-maximum-abs-sum-route}
Let
$$
M=(X,Y,W_X,W_Y,D,S,A,U,R,E,H,C,P,N)
$$
be an accepted $\RegularCauchyMaximumUp$ carrier. Every $\RealUp$ consumer of the maximum row reaches the seal $E$ only through the constructive route
$$
\begin{aligned}
&\text{aligned windows for }X\text{ and }Y,\\
&\text{dyadic subtraction }X-Y,\\
&\text{regular Cauchy difference }S,\\
&\text{absolute difference }A,\\
&\text{regular Cauchy sum of }X,Y,A,\\
&\text{dyadic half-sum readback }R,\\
&\text{final real seal }E.
\end{aligned}
$$
Equivalently, the packet presents the maximum of $X$ and $Y$ by the displayed finite route for $(X+Y+|X-Y|)/2$, and it exposes no quotient stream equality, selected limit, trichotomy, countable choice, host maximum, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with a real-facing read of the carrier. By the obligation rows of \autoref{thm:regular-cauchy-maximum-namecert-obligations}, the read cannot reach the seal $E$ before it has consumed the half-sum readback row $R$.

The row $R$ is downstream of the sum row $U$. The sum row consumes the two source names together with the absolute-difference row $A$, and the row $A$ is downstream of the regular Cauchy difference row $S$ formed from the dyadic subtraction ledger $D$.

The ledger $D$ is read only after the aligned windows $W_X$ and $W_Y$ are displayed. Thus the route is the listed sequence of aligned windows, dyadic subtraction, regular Cauchy difference, absolute difference, sum, half-sum readback, and real seal.

No excluded principle has a coordinate in the carrier. The provenance and replay rows merely name and transport this finite route, so the consumer receives the abs-sum maximum certificate and nothing outside it.
\end{proof}

\closureat{RegularCauchyMaximumUp}{seedStr}

\begin{closurestatus}{\RegularCauchyMaximumUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-maximum-carrier}, \autoref{thm:regular-cauchy-maximum-namecert-obligations}, and \autoref{thm:regular-cauchy-maximum-abs-sum-route} seed a finite upper-member route for two regular Cauchy real names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host maximum, trichotomy, quotient stream equality, selected limits, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, aligned-window exposure, arithmetic route exactness, classifier stability, non-escape, and the abs-sum RealUp handoff for BEDC.Derived.RegularCauchyMaximumUp.}
  \constructivestory{A $\RegularCauchyMaximumUp$ packet is generated from two regular Cauchy Real rows, aligned StreamName windows, a DyadicRatCore subtraction ledger, RegularCauchyDifference, RegularCauchyAbs, and RegularCauchySum rows, a dyadic half-sum readback, a RealUp seal, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
\end{closurestatus}
