\chapter{A Concrete Naming Certificate for $\CauchyCompletionEliminatorUp$}
\label{ch:concrete-instances-cauchy-completion-eliminator-namecert}
\origin{human}

Following Bishop--Bridges constructive completion and the Mac Lane--Eilenberg--Moore vocabulary of recursion from an algebraic completion object, the $\CauchyCompletionEliminatorUp$ packet records the BEDC eliminator interface for reading out of a Cauchy completion. It sits after the completion monad of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, the Kleisli consumer route of \autoref{ch:concrete-instances-cauchy-completion-kleisli-namecert}, the functorial action of \autoref{ch:concrete-instances-cauchy-completion-functoriality-namecert}, and the algebra boundary of \autoref{ch:concrete-instances-cauchy-completion-algebra-namecert}. Its analytic input surface is the finite stream window of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}.

The packet is an eliminator boundary, not a representative selector. It exposes exactly the finite rows needed to extend a dense-source action through regular Cauchy tails and to compare the resulting completed reads by tail agreement.

\begin{definition}[Cauchy completion eliminator carrier]
\label{def:cauchy-completion-eliminator-carrier}
A $\CauchyCompletionEliminatorUp$ carrier is a finite $\BHist$ packet
$$
E=(D,T,M,A,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the dense source data row, displaying the source NameCert, its finite $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback rows, and the $\DyadicRatCoreUp$ tolerance observations before any completed read is inspected.
\item $T$ is the target NameCert data row, including the codomain carrier surface, its accepted equality classifier, and the local naming row for the target of the eliminator.
\item $M$ is the Cauchy-continuity modulus row, recording how a finite dyadic tolerance request on the target read is answered by a finite tail request on the dense source data.
\item $A$ is the extension action row, sending an accepted regular Cauchy tail over $D$ to a target packet over $T$ by the modulus-controlled route $M$.
\item $U$ is the uniqueness-by-tail-agreement ledger: two extension actions over the same dense-source action and the same modulus are compared by displayed $\hsame$ equivalence of their regular tails.
\item $H$ records componentwise $\hsame$ transport for the dense source data, target NameCert data, Cauchy-continuity modulus, extension action, uniqueness ledger, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay of the route
$$
D,T,M \longmapsto A \longmapsto U \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionEliminatorUp$, $\CauchyCompletionMonadUp$, $\CauchyCompletionKleisliUp$, $\CauchyCompletionFunctorialityUp$, $\CauchyCompletionAlgebraUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionEliminatorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,T,M,A,U,H,C,P,N$. The carrier has no coordinate for quotient representatives, host equality of completed objects, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Cauchy completion eliminator NameCert obligations]
\label{thm:cauchy-completion-eliminator-namecert-obligations}
For every accepted $\CauchyCompletionEliminatorUp$ carrier
$$
E=(D,T,M,A,U,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionEliminatorUp}$ surface consists exactly of the following five finite obligation rows:
\begin{enumerate}
\item carrier admission for the dense source data, target NameCert data, Cauchy-continuity modulus, extension action, uniqueness ledger, transport, replay, provenance, and local naming row;
\item dense-source action stability, requiring the action on displayed dense rows to be invariant under the carried $\hsame$ transport of $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ observations;
\item modulus-controlled extension, requiring every completed-route read to pass through the modulus row $M$ before the extension action row $A$ is inspected;
\item uniqueness through Cauchy tail agreement, requiring two completed reads over the same dense action and modulus to be compared only through the ledger $U$ and displayed $\hsame$ equivalence of regular tails;
\item refusal of quotient representatives, host equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking as local obligation data.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-eliminator-carrier}. The accepted packet displays exactly the dense source data, target NameCert data, modulus, action, uniqueness ledger, and structural rows.

Dense-source stability is read from $D$ and $H$. The dense action can inspect only finite stream windows, regular rational readback, and dyadic tolerance observations, and componentwise transport preserves those displayed rows before any target packet is named.

The extension clause is supplied by $M$ and $A$. A completed-route consumer first presents a target tolerance request to the modulus row, receives a finite tail request on the dense source, and then applies the extension action to that displayed tail.

Uniqueness is supplied by $U$. When two accepted actions have the same dense-source action and the same modulus, the only comparison row available is tail agreement of the regular Cauchy presentations through displayed $\hsame$ routes.

The refusal clause is structural. Since no excluded object appears as a coordinate of $E$, the replay, provenance, and local naming rows cannot export quotient representatives, host equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{proof}

\begin{theorem}[Cauchy completion eliminator uniqueness]
\label{thm:cauchy-completion-eliminator-uniqueness}
Let
$$
E=(D,T,M,A,U,H,C,P,N)
\quad\text{and}\quad
E'=(D',T',M',A',U',H',C',P',N')
$$
be accepted $\CauchyCompletionEliminatorUp$ packets. If $E$ and $E'$ display the same dense-source action, the same Cauchy-continuity modulus, and componentwise $\hsame$ transport of the target NameCert rows, then the two eliminator packets are classifier-equal on every completed route whose regular tails are $\hsame$-equivalent. The comparison is exhausted by the uniqueness ledgers $U,U'$ and the displayed tail-agreement rows; it does not pass through quotient representatives, host equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Project both accepted carriers. The hypotheses identify the dense-source action and the modulus rows, so any completed-route read issued to $E$ and $E'$ produces the same finite tail request on the dense source.

Now compare the regular tails. The assumed $\hsame$ equivalence of those tails is exactly the input consumed by the uniqueness ledgers $U$ and $U'$. These ledgers compare the two target reads through the carried target NameCert transport, not through host equality of completed objects.

The structural rows finish the classifier comparison. Componentwise transport $H,H'$, replay $C,C'$, provenance $P,P'$, and local names $N,N'$ preserve the same dense action, modulus, and tail-agreement route. Since the carriers contain no excluded coordinate, the classifier equality cannot appeal to quotient representatives, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{proof}

\closureat{CauchyCompletionEliminatorUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionEliminatorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-eliminator-carrier}, \autoref{thm:cauchy-completion-eliminator-namecert-obligations}, and \autoref{thm:cauchy-completion-eliminator-uniqueness} seed the finite eliminator surface for Cauchy-completion reads out of regular tails.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient representatives, host equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-source action stability, modulus-controlled extension, uniqueness through Cauchy tail agreement, and non-escape proofs for BEDC.Derived.CauchyCompletionEliminatorUp.}
  \constructivestory{A $\CauchyCompletionEliminatorUp$ packet is generated from dense source data, target NameCert data, a Cauchy-continuity modulus, an extension action, a uniqueness-by-tail-agreement ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
