\chapter{A Concrete Naming Certificate for $\RealCompletionReflectionUp$}
\label{ch:concrete-instances-real-completion-reflection-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and Kelley completion terminology, the $\RealCompletionReflectionUp$ packet names the boundary at which displayed completion data may be consumed as a terminal $\RealUp$ seal. It reads the finite $\StreamNameUp$ windows of \autoref{ch:concrete-instances-streamname-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the $\RegSeqRatUp$ rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, and the completion-reflection surface of \autoref{ch:concrete-instances-completionreflection-namecert}. The certificate isolates the handoff from displayed completion rows to Real-facing consumption; it does not form quotient completions, select host limits, compare host real equality, assume countable choice, branch by trichotomy, or import ambient $\RealUp$ completeness.

\begin{definition}[RealCompletionReflection carrier]
\label{def:real-completion-reflection-carrier}
A $\RealCompletionReflectionUp$ carrier is a finite $\BHist$ packet
$$
X=(C,R,S,D,E,F,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the displayed completion data row. It records the source completion request, finite approximation schedule, and completion-facing consumer slot before any Real seal is read.
\item $R$ is the $\RegSeqRatUp$ readback row generated from the displayed completion data and used as the rational surface for the terminal seal.
\item $S$ is the $\StreamNameUp$ window family opened by the same readback request, with one finite window for each rational observation consumed by $R$ or by a Real-facing consumer.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording dyadic scale, slack, radius, and comparison rows for the windows in $S$.
\item $E$ is the terminal $\RealUp$ seal. It is readable only after $C,R,S,D,F,H,K,P,N$ have exposed the completion source, finite windows, dyadic tolerance data, and reflection route.
\item $F$ is the reflection row. It identifies the completion-facing route with the Real-facing read without adding quotient representatives, selected limits, host equality, choice data, trichotomy branches, or ambient completeness.
\item $H$ records componentwise $\hsame$ transport for completion data, rational readback, stream windows, dyadic tolerance ledger, Real seal, reflection row, replay, provenance, and local naming.
\item $K$ records displayed $\Cont$ replay from every Real-facing completion request through $C,R,S,D,F,H,P,N$ before the seal $E$ is inspected.
\item $P$ is the $\Pkg$ provenance over $\RealCompletionReflectionUp$, $\CompletionReflectionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealCompletionReflectionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $C,R,S,D,E,F,H,K,P,N$. It has no coordinate for quotient completions, selected limits, host real equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.RealCompletionReflectionUp.RealCompletionReflectionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RealCompletionReflection NameCert obligations]
\label{thm:real-completion-reflection-namecert-obligations}
For every accepted $\RealCompletionReflectionUp$ carrier
$$
X=(C,R,S,D,E,F,H,K,P,N),
$$
the local $\NameCert_{\RealCompletionReflectionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed completion data, regular rational readback, finite stream windows, dyadic tolerance ledger, terminal Real seal, reflection row, transport, replay, provenance, and local naming;
\item completion-source exposure, requiring every Real-facing read to display its completion source in $C$ before any rational readback, stream window, dyadic tolerance, or seal coordinate is inspected;
\item RegSeqRat, StreamName, and DyadicRatCore handoff, requiring $R,S,D$ to expose the same finite rational observations, window bounds, dyadic scales, slack data, and comparison rows used by the requested completion read;
\item RealUp seal non-escape, requiring $E$ to be read only after $C,R,S,D,F,H,K,P,N$ have fixed the displayed completion route and forbidding any direct appeal to quotient completions, selected limits, host real equality, countable choice, trichotomy, or ambient completeness;
\item reflection-ledger exactness, requiring $F,H,K,P,N$ to transport, replay, source, and name exactly the displayed rows $C,R,S,D,E$ and no hidden completion or Real data.
\end{enumerate}
No RealCompletionReflection obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-completion-reflection-carrier}. The accepted packet displays one completion-source row, one regular rational readback, one finite stream-window family, one dyadic tolerance ledger, one terminal Real seal, one reflection row, and the structural rows that transport, replay, source, and name them.

Completion-source exposure is read from $C$. Since the carrier has no second completion coordinate, every Real-facing read begins with the displayed completion request before it can inspect rational, stream, dyadic, or seal data.

The finite handoff is read from $R,S,D$. The regular rational readback $R$ consumes exactly the finite windows $S$, and those windows are measured by the dyadic tolerance ledger $D$. Thus every rational observation seen by a Real-facing consumer is already present in the displayed finite route.

The Real seal is terminal. The coordinate $E$ is exposed only after the reflection row $F$ and the structural rows $H,K,P,N$ have fixed the route through $C,R,S,D$. Because the packet contains no quotient completion, selected limit, host equality, choice schedule, trichotomy branch, or ambient completeness theorem, the seal cannot escape that route.

Finally, $F,H,K,P,N$ add no analytic data beyond the displayed rows. They identify the reflection route, transport it componentwise, replay it through $\Cont$, record provenance, and name the local certificate. Hence the five listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[RealCompletionReflection Real seal handoff]
\label{thm:real-completion-reflection-real-seal-handoff}
Let
$$
X=(C,R,S,D,E,F,H,K,P,N)
$$
be an accepted $\RealCompletionReflectionUp$ carrier. Every Real-facing consumer of the completion data factors through
$$
C \longmapsto R \longmapsto S \longmapsto D \longmapsto F \longmapsto H,K,P,N
$$
before reading the terminal seal $E$. Consequently the consumer cannot obtain a $\RealUp$ value from quotient completions, selected limits, host real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Fix a Real-facing consumer of $X$. The only Real-seal coordinate in the carrier is $E$, so any consumer that reaches a Real-facing value must eventually read that terminal coordinate.

Read the dependency route in the carrier. The completion source is displayed by $C$, the regular rational readback is $R$, the finite stream-window family is $S$, and the dyadic tolerance ledger is $D$. These rows provide the finite completion data that a Real-facing consumer can inspect.

The reflection and structural rows precede the seal read. The row $F$ identifies the completion-facing route with the Real-facing route, while $H$ transports the displayed coordinates, $K$ replays them through $\Cont$, and $P,N$ source and name the package.

No further analytic coordinate remains. Since quotient completions, selected limits, host real equality, countable choice, trichotomy, and ambient completeness are absent from the carrier, every Real-facing consumer must factor through $C,R,S,D,F,H,K,P,N$ before reading $E$.
\end{proof}

\closureat{RealCompletionReflectionUp}{seedStr}

\begin{closurestatus}{\RealCompletionReflectionUp}
  \constructivestory{A $\RealCompletionReflectionUp$ packet is generated from displayed completion data, RegSeqRat readback, StreamName windows, a DyadicRatCore tolerance ledger, a terminal RealUp seal, a reflection row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-completion-reflection-carrier}, \autoref{thm:real-completion-reflection-namecert-obligations}, and \autoref{thm:real-completion-reflection-real-seal-handoff} seed the finite reflection boundary from displayed completion data to terminal Real-facing consumption.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.RealCompletionReflectionUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected limits, host real equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, completion-source exposure, RegSeqRat, StreamName, and DyadicRatCore handoff, RealUp seal non-escape, reflection-ledger exactness, transport, replay, provenance, and local naming for BEDC.Derived.RealCompletionReflectionUp.}
\end{closurestatus}
