\chapter{A Concrete Naming Certificate for $\DyadicMetricTriangleUp$}
\label{ch:concrete-instances-dyadic-metric-triangle-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DyadicMetricTriangleUp$ packet names the finite three-point dyadic triangle ledger that must be visible before regular rational names, real-name seals, or metric-space consumers may use a triangle estimate. It reads the three displayed dyadic endpoints of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the nonnegative endpoint discipline of \autoref{ch:concrete-instances-dyadicabsolutevalue-namecert}, and the distance-ledger packet of \autoref{ch:concrete-instances-dyadic-metric-namecert}; it hands the resulting bound to \autoref{ch:concrete-instances-regseqrat-namecert} and then to \autoref{ch:concrete-instances-real-namecert}. The chapter isolates the triangle inequality as a finite comparison route, not as a law imported from a host metric space.

\begin{definition}[Dyadic metric triangle carrier]
\label{def:dyadic-metric-triangle-carrier}
A $\DyadicMetricTriangleUp$ carrier is a finite $\BHist$ packet
$$
T=(x,y,z,dxy,dyz,dxz,a,b,t,h,c,p,n)
$$
with the following displayed rows:
\begin{enumerate}
\item $x,y,z$ are the three accepted $\DyadicRatCoreUp$ endpoint rows, including their visible mantissa, denominator, $\IntUp$, and $\RatUp$ provenance.
\item $dxy,dyz,dxz$ are the three dyadic distance ledgers for the pairs $(x,y)$, $(y,z)$, and $(x,z)$. Each ledger records its common-denominator subtraction window, dyadic radius row, and finite comparison data through the $\DyadicMetricUp$ packet.
\item $a$ records the $\DyadicAbsoluteValueUp$ endpoint rows attached to the three distance ledgers, so every nonnegative distance endpoint is read through the absolute-value packet rather than through a host absolute-value function.
\item $b$ is the displayed comparison row
$$
dxz \leq dxy + dyz .
$$
It records the common-denominator addition window, the dyadic upper-bound ledger, and the finite order comparison witnessing the triangle bound.
\item $t$ is the downstream handoff row. It exposes the finite route from the three endpoints through the three distance ledgers, the absolute-value endpoints, and the comparison row to $\RegSeqRatUp$, $\RealUp$, and $\MetricSpaceUp$ consumers.
\item $h$ records componentwise $\hsame$ transport for the endpoint rows, distance ledgers, absolute-value rows, comparison row, consumer handoff, replay, provenance, and local naming.
\item $c$ records displayed $\Cont$ replay from the endpoint rows through distance, absolute value, comparison, consumer handoff, transport, provenance, and local naming.
\item $p$ is the $\Pkg$ provenance over $\DyadicMetricTriangleUp$, $\DyadicRatCoreUp$, $\DyadicMetricUp$, $\DyadicAbsoluteValueUp$, $\RegSeqRatUp$, $\RealUp$, $\MetricSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $n$ is the local $\NameCert_{\DyadicMetricTriangleUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $x,y,z,dxy,dyz,dxz,a,b,t,h,c,p,n$. It has no coordinate for host metric spaces, quotient rationals, trichotomy, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Dyadic metric triangle NameCert obligations]
\label{thm:dyadic-metric-triangle-namecert-obligations}
For every accepted $\DyadicMetricTriangleUp$ carrier $T=(x,y,z,dxy,dyz,dxz,a,b,t,h,c,p,n)$, the local $\NameCert_{\DyadicMetricTriangleUp}$ surface consists exactly of the following five rows:
\begin{enumerate}
\item carrier admission for the displayed endpoints $x,y,z$ and the three distance ledgers $dxy,dyz,dxz$;
\item absolute-value exposure through $a$ for each nonnegative dyadic distance endpoint;
\item triangle comparison through the row $b$ witnessing $dxz \leq dxy + dyz$;
\item consumer handoff through $t$ to $\RegSeqRatUp$, $\RealUp$, and $\MetricSpaceUp$;
\item componentwise structural replay through $h,c,p,n$.
\end{enumerate}
No triangle-bound obligation is stored outside those finite rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dyadic-metric-triangle-carrier}. The visible packet lists three $\DyadicRatCoreUp$ endpoint rows and three $\DyadicMetricUp$ distance ledgers before any comparison row is available.

The nonnegative endpoint data is not a host operation. It is routed through the $\DyadicAbsoluteValueUp$ rows in $a$, one for each displayed distance ledger.

The triangle row is the only comparison row. It displays the dyadic addition ledger and the finite order comparison for $dxz \leq dxy + dyz$, so the packet has no hidden metric-law coordinate.

The consumer and structural rows are terminal. Rows $t,h,c,p,n$ hand off, transport, replay, package, and name the displayed triangle ledger without adding quotient rationals, trichotomy, selected limits, ambient completeness, Lean verification, or bridge checking.
\end{proof}

\begin{theorem}[Dyadic metric triangle RegSeqRat handoff]
\label{thm:dyadic-metric-triangle-regseqrat-handoff}
Every $\RegSeqRatUp$, $\RealUp$, or $\MetricSpaceUp$ consumer of an accepted $\DyadicMetricTriangleUp$ triangle bound must pass through the finite route
$$
x,y,z \longmapsto dxy,dyz,dxz \longmapsto a \longmapsto b \longmapsto t \longmapsto h,c,p,n
$$
before the triangle estimate is available as a regular-rational tolerance bound, a real-name distance surface, or a metric witness. Consequently no such consumer can obtain the triangle bound through a host metric space, quotient rational equality, trichotomy, selected limit, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only consumer-facing coordinate is $t$, and $t$ is downstream of the endpoint rows, the three dyadic distance ledgers, the absolute-value endpoint rows, and the comparison row.

For a $\RegSeqRatUp$ consumer, the triangle estimate is read as a finite dyadic tolerance comparison. The comparison cannot be inspected until the three distance ledgers and the absolute-value endpoint route have displayed the row $dxz \leq dxy + dyz$.

For a $\RealUp$ or $\MetricSpaceUp$ consumer, the same route is terminal. The real-name seal and the metric witness receive only the surface exposed by $t$, while $h,c,p,n$ transport, replay, package, and name that surface without introducing a second metric law.

The excluded objects are absent from the carrier. Thus every accepted downstream read factors through the displayed triangle ledger.
\end{proof}

\closureat{DyadicMetricTriangleUp}{seedStr}

\begin{closurestatus}{\DyadicMetricTriangleUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{thm:dyadic-metric-triangle-namecert-obligations} and \autoref{thm:dyadic-metric-triangle-regseqrat-handoff} seed the finite dyadic triangle route from three $\DyadicRatCoreUp$ endpoints through three distance ledgers, absolute-value endpoints, the displayed comparison row, consumer handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host metric spaces, quotient rationals, trichotomy, selected limits, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, three-distance ledger exposure, absolute-value endpoint exposure, triangle comparison, consumer handoff, provenance, transport, replay, and local naming for BEDC.Derived.DyadicMetricTriangleUp.}
  \constructivestory{A $\DyadicMetricTriangleUp$ packet is generated from three $\DyadicRatCoreUp$ endpoint rows, three $\DyadicMetricUp$ distance ledgers, $\DyadicAbsoluteValueUp$ endpoint rows, one dyadic triangle comparison row, a $\RegSeqRatUp$, $\RealUp$, and $\MetricSpaceUp$ consumer handoff, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
