\chapter{Dedekind Cauchy Sandwich NameCert Construction}
\label{ch:concrete-instances-dedekind-cauchy-sandwich-namecert}
\origin{human}

Following Bishop and Bridges on constructive real representations, the $\DedekindCauchySandwichUp$ packet records the finite sandwich used when located-cut evidence is compared with a regular-Cauchy name before the terminal real seal is consumed. It sits between the lower and upper cut rows of \autoref{ch:concrete-instances-locatedcut-namecert}, the comparison route of \autoref{ch:concrete-instances-dedekind-cauchy-comparison-namecert}, and the interval enclosure surface of \autoref{ch:concrete-instances-located-real-interval-namecert}. Its downstream handoff is the regular-rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only finite carrier, regularization, transport, replay, provenance, and local NameCert rows; it does not claim a quotient cut, selected supremum, trichotomy, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Dedekind Cauchy sandwich carrier]
\label{def:dedekind-cauchy-sandwich-carrier}
A $\DedekindCauchySandwichUp$ carrier is a finite $\BHist$ packet
$$
S=(L,U,I,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the lower located-cut row, recording finite dyadic witnesses below the inspected located cut.
\item $U$ is the upper located-cut row, recording finite dyadic witnesses above the same inspected located cut.
\item $I$ is the dyadic interval enclosure row, binding each visible unary precision to an interval whose lower endpoint is certified by $L$ and whose upper endpoint is certified by $U$.
\item $W$ is the finite $\StreamNameUp$ window family opened only after the corresponding lower, upper, and interval rows have been displayed.
\item $R$ is the $\RegSeqRatUp$ handoff row assembled from the displayed stream windows and dyadic enclosure budgets.
\item $E$ is the terminal $\RealUp$ seal row reached only through $L,U,I,W,R$.
\item $H$ records componentwise $\hsame$ transport for the lower row, upper row, interval enclosure, stream windows, regular handoff, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
L,U \longmapsto I \longmapsto W \longmapsto R \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\DedekindCauchySandwichUp$, $\LocatedCutUp$, $\DedekindCauchyComparisonUp$, $\LocatedRealIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindCauchySandwichUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,U,I,W,R,E,H,C,P,N$. It has no coordinate for quotient cuts, selected suprema, trichotomy, countable choice, host completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.DedekindCauchySandwichUp.DedekindCauchySandwichTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Dedekind Cauchy sandwich regularization]
\label{thm:dedekind-cauchy-sandwich-regularization}
For every accepted $\DedekindCauchySandwichUp$ carrier
$$
S=(L,U,I,W,R,E,H,C,P,N),
$$
each visible unary precision exported by $S$ has a displayed $\RegSeqRatUp$ handoff row $R$ squeezed between the lower and upper located-cut rows $L$ and $U$ through the dyadic interval enclosure row $I$ and the finite $\StreamNameUp$ windows $W$. The regular-Cauchy read is obtained without quotient-cut equality, selected suprema, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:dedekind-cauchy-sandwich-carrier}. The only lower and upper cut data available to a precision request are the displayed rows $L$ and $U$.

The interval row $I$ binds those two rows at the same visible unary precision. Its lower endpoint is certified by $L$, its upper endpoint is certified by $U$, and the carrier has no separate coordinate from which a detached bound could be read.

The stream and regular-Cauchy rows are downstream of that enclosure. The finite windows $W$ are opened after $I$, and the regular handoff $R$ is assembled from those windows and the same dyadic enclosure budgets.

Finally, $H,C,P,N$ transport, replay, source, and name the displayed route only. Since the carrier contains no quotient cut, selected supremum, trichotomy witness, countable-choice row, or ambient completeness coordinate, every exported regular-Cauchy read is squeezed between the displayed lower and upper rows through $I$ and $W$.
\end{proof}

\begin{theorem}[Dedekind Cauchy sandwich NameCert obligations]
\label{thm:dedekind-cauchy-sandwich-namecert-obligations}
For every accepted $\DedekindCauchySandwichUp$ carrier
$$
S=(L,U,I,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\DedekindCauchySandwichUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed lower located-cut row, upper located-cut row, dyadic interval enclosure, stream windows, regular-Cauchy handoff, Real seal, transport, replay, provenance, and local naming rows;
\item lower-upper disjointness, requiring the lower and upper rows to appear as separated faces of the same finite located-cut observation before any interval or stream row is read;
\item locatedness, requiring each visible unary precision to display a dyadic enclosure row $I$ whose endpoints are sourced from $L$ and $U$;
\item regularization, requiring $R$ to be assembled from the finite windows $W$ opened over the displayed enclosure rather than from a detached Cauchy representative;
\item classifier transport, requiring componentwise $\hsame$ transport to preserve the lower row, upper row, enclosure row, stream windows, handoff row, Real seal, replay, provenance, and local NameCert row together;
\item ledger exclusion, requiring the packet to expose no quotient cut, selected supremum, trichotomy witness, countable-choice row, ambient $\RealUp$ completeness principle, Lean verification, or bridge credential.
\end{enumerate}
No $\DedekindCauchySandwichUp$ obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is the projection of the packet $S=(L,U,I,W,R,E,H,C,P,N)$ to its ten displayed coordinates. These coordinates are the whole accepted carrier inventory.

Lower-upper disjointness and locatedness are read through $L,U,I$. The two located-cut faces are displayed before the interval enclosure is available, and each visible unary precision receives its enclosure from that same pair of rows.

Regularization is the projection to $W$ and $R$. The stream windows are opened over the displayed enclosure, and the regular-Cauchy handoff is downstream of those windows rather than a free-standing representative.

Classifier transport is the projection to $H$ together with the replay and provenance rows $C$ and $P$. These rows preserve the displayed coordinates componentwise and do not introduce a second classifier surface.

The ledger exclusion row is therefore exhaustive. Since no excluded coordinate appears in the carrier, the local NameCert can only certify the displayed sandwich route and cannot export quotient-cut equality, selected suprema, trichotomy, countable choice, ambient completeness, Lean verification, or bridge checking.
\end{proof}

\closureat{DedekindCauchySandwichUp}{seedStr}

\begin{closurestatus}{\DedekindCauchySandwichUp}
  \constructivestory{A $\DedekindCauchySandwichUp$ packet is generated from lower and upper located-cut rows, dyadic interval enclosure rows, finite StreamName windows, a RegSeqRat handoff, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-cauchy-sandwich-carrier}, \autoref{thm:dedekind-cauchy-sandwich-regularization}, and \autoref{thm:dedekind-cauchy-sandwich-namecert-obligations} seed the finite located-cut to regular-Cauchy sandwich packet used by Real representation comparison.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient cuts, selected suprema, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, regularization, classifier transport, ledger exclusion, and local NameCert proofs for BEDC.Derived.DedekindCauchySandwichUp.}
\end{closurestatus}
