\chapter{A Concrete Naming Certificate for $\CantorBendixsonUp$}
\label{ch:concrete-instances-cantor-bendixson-namecert}
\origin{human}

Following Cantor and Bendixson's derived-set theorem in the constructive closed-set reading, the $\CantorBendixsonUp$ packet records a finite derivative-stage route for a displayed closed subset of the real line before any completion-facing consumer reads the retained kernel or the isolated-point ledger. It consumes the finite real-boundary chapters \autoref{ch:concrete-instances-cantor-completeness-namecert}, \autoref{ch:concrete-instances-cantor-intersection-namecert}, \autoref{ch:concrete-instances-located-real-nested-intervals-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names only the finite derivative data exposed by the carrier; it does not import the transfinite Cantor-Bendixson decomposition, choice of isolated points, quotient real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Cantor-Bendixson finite derivative carrier]
\label{def:cantor-bendixson-carrier}
A $\CantorBendixsonUp$ carrier is a finite $\BHist$ packet
$$
B=(F,D,I,K,W,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the closed-set row. It records the displayed finite closed-set observations, interval enclosures, and located boundary reads supplied to the derivative packet.
\item $D$ is the derivative-stage row. It names the finite stage budget and the finite successor-stage ledger used to pass from the current closed row to the next derived row.
\item $I$ is the isolated-point ledger. It records only isolated points whose witnessing separating intervals, dyadic radii, and stage membership checks are displayed inside the packet.
\item $K$ is the retained perfect-kernel row at the displayed finite stage. It is read as the residual closed row after the isolated ledger and derivative-stage rows have been consumed.
\item $W$ is the $\StreamNameUp$ window family through which the closed-set observations, isolating intervals, and retained-kernel reads are exposed to finite consumers.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same windows and derivative-stage ledger.
\item $Q$ is the $\DyadicRatCoreUp$ ledger for the radii, comparisons, interval separations, and containment checks used by $F,D,I,K,W,R$.
\item $E$ is the terminal $\RealUp$ seal boundary for the displayed closed-set and retained-kernel reads.
\item $H$ records componentwise $\hsame$ transport for the closed-set, derivative-stage, isolated-ledger, kernel, window, readback, dyadic, Real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of every consumer request through
$$
F,D\longmapsto I,K\longmapsto W,Q\longmapsto R\longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\CantorBendixsonUp$, $\CantorCompletenessUp$, $\CantorIntersectionUp$, $\LocatedRealNestedIntervalsUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CantorBendixsonUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,D,I,K,W,R,Q,E,H,C,P,N$. It has no coordinate for a transfinite rank, a selected isolated-point enumeration, quotient real equality, countable choice, host closed-set equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cantor-Bendixson NameCert obligations]
\label{thm:cantor-bendixson-namecert-obligations}
For every accepted $\CantorBendixsonUp$ carrier $B=(F,D,I,K,W,R,Q,E,H,C,P,N)$, the local $\NameCert_{\CantorBendixsonUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item carrier admission for the displayed closed-set, derivative-stage, isolated-ledger, retained-kernel, StreamName, RegSeqRat, DyadicRatCore, Real-seal, transport, replay, provenance, and local naming rows;
\item derivative-stage classifier stability, requiring accepted comparisons to preserve the finite stage budget and every displayed successor-stage derived-row check;
\item isolated-point ledger exactness, requiring each listed isolated point to carry its displayed separating interval, dyadic radius, and membership row, with no hidden selector for further isolated points;
\item retained-kernel handoff, requiring $K$ to be downstream of the displayed derivative-stage and isolated-ledger rows before any StreamName, RegSeqRat, DyadicRatCore, or Real consumer reads it;
\item ledger nonescape, requiring $W,R,Q,E,H,C,P,N$ to expose only the rows already displayed in $F,D,I,K$ and to export no transfinite decomposition, selected enumeration, quotient real equality, countable choice, host closed-set equality, or ambient completeness.
\end{enumerate}
No Cantor-Bendixson NameCert obligation is stored outside these rows.
\end{theorem}
\leanchecked{BEDC.Derived.CantorBendixsonUp.CantorBendixsonTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the accepted carrier $B=(F,D,I,K,W,R,Q,E,H,C,P,N)$. Carrier admission exposes exactly the closed-set row, finite derivative-stage row, isolated-point ledger, retained-kernel row, observation windows, regular readback, dyadic ledger, Real seal, and the structural rows.

The derivative-stage clause is finite. The row $D$ records the stage budget and successor-stage checks, while $H$ transports those checks componentwise and $C$ replays them before the kernel row is inspected.

The isolated-point clause is also finite. Each entry in $I$ carries its separating interval, dyadic radius, and membership check through $Q$, so the ledger lists displayed witnesses rather than a choice-selected enumeration.

The retained-kernel handoff follows from the placement of $K$ after $F,D,I$ and before $W,R,Q,E$. A consumer reaches the kernel only by the route recorded in the carrier.

Finally, provenance and local naming package the same rows. Since no carrier coordinate contains a transfinite rank, quotient real equality, countable choice, host closed-set equality, or ambient completeness theorem, the five listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cantor-Bendixson finite derivative handoff]
\label{thm:cantor-bendixson-finite-derivative-handoff}
Every $\RealUp$-facing read of an accepted $\CantorBendixsonUp$ carrier factors through the finite route displayed by \autoref{ch:concrete-instances-cantor-completeness-namecert}, \autoref{ch:concrete-instances-cantor-intersection-namecert}, \autoref{ch:concrete-instances-located-real-nested-intervals-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. Concretely, a consumer of $B=(F,D,I,K,W,R,Q,E,H,C,P,N)$ must read the closed-set row, finite derivative-stage ledger, isolated-point ledger, retained-kernel row, StreamName windows, RegSeqRat readback, DyadicRatCore comparisons, transport, replay, provenance, and local naming before the Real seal $E$ is exposed.
\end{theorem}
\begin{proof}
Begin with a completion-facing request for the Real seal. Carrier projection shows that the only terminal Real-facing coordinate is $E$, and the continuation row $C$ routes every access to $E$ through the displayed packet.

The closed-set and derivative rows are read first. Their finite nested and interval observations are the part of the route governed by the Cantor completeness, Cantor intersection, and located real nested-interval chapters.

Next the request passes through the isolated-point ledger $I$ and retained-kernel row $K$. The listed isolating intervals and residual closed row are exposed only by the finite stage route, not by a transfinite decomposition or a selector.

The observation and arithmetic rows then pass through $W,R,Q$. These are exactly the StreamName, RegSeqRat, and DyadicRatCore surfaces consumed before the terminal Real boundary.

The structural rows $H,P,N$ bind the same path under transport, provenance, and local naming. Hence every Real-facing read factors through the seven cited finite boundary chapters and exports none of the excluded classical or quotient data.
\end{proof}

\closureat{CantorBendixsonUp}{seedStr}

\begin{closurestatus}{\CantorBendixsonUp}
  \constructivestory{A $\CantorBendixsonUp$ packet is generated from a displayed closed-set row, a finite derivative-stage row, an isolated-point ledger, a retained perfect-kernel row, StreamName windows, RegSeqRat readback, DyadicRatCore comparison data, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cantor-bendixson-carrier}, \autoref{thm:cantor-bendixson-namecert-obligations}, and \autoref{thm:cantor-bendixson-finite-derivative-handoff} seed the finite Cantor-Bendixson derivative route from closed-set observations through displayed isolated-point ledgers and retained-kernel rows to Real-facing seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close the full transfinite Cantor-Bendixson decomposition, selected isolated points, quotient real equality, choice, ambient $\RealUp$ completeness, Lean theorem coverage, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, derivative-stage classifier stability, isolated-point ledger exactness, retained-kernel handoff, ledger nonescape, and Real-facing handoff for BEDC.Derived.CantorBendixsonUp.}
\end{closurestatus}
