\chapter{A Concrete Naming Certificate for $\DyadicOscillationModulusUp$}
\label{ch:concrete-instances-dyadic-oscillation-modulus-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, an oscillation modulus is read as finite information about how a displayed tolerance request is answered by a displayed tail window. The $\DyadicOscillationModulusUp$ packet records that information at the dyadic level: it sits between the raw Cauchy oscillation ledger of \autoref{ch:concrete-instances-cauchyoscillation-namecert} and the Real-facing oscillation consumer of \autoref{ch:concrete-instances-real-oscillation-namecert}. Its numerical source rows are the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}.

The packet is not a quotient stream, a selected limit, or a host equality statement. It is a finite NameCert row whose classifier can inspect only a dyadic precision request, a threshold schedule, a tail-window ledger, a regular rational readback, a CauchyOscillation source row, a RealOscillation consumer row, a Real seal handoff, and the displayed transport, replay, provenance, and local naming rows.

\begin{definition}[Dyadic oscillation modulus carrier]
\label{def:dyadic-oscillation-modulus-carrier}
A $\DyadicOscillationModulusUp$ carrier is a finite $\BHist$ packet
$$
M_{\mathrm{osc}}=(D,\mu,W,R,O,Q,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ tolerance row naming the dyadic radius requested by an oscillation consumer.
\item $\mu$ is the finite modulus schedule row. It answers the request named by $D$ with a displayed tail threshold and records no external choice function.
\item $W$ is the $\StreamNameUp$ tail-window row opened at the threshold supplied by $\mu$.
\item $R$ is the $\RegSeqRatUp$ readback row that repacks the window observations of $W$ as regular rational data before any real-facing conclusion is exposed.
\item $O$ is the $\CauchyOscillationUp$ source ledger whose tail comparisons are certified at the tolerance $D$ over the window $W$.
\item $Q$ is the $\RealOscillationUp$ consumer row that receives the same dyadic tolerance, window, readback, and Cauchy oscillation ledger.
\item $S$ is the $\RealUp$ seal handoff reached only after $D,\mu,W,R,O,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the dyadic tolerance, modulus schedule, stream window, regular rational readback, CauchyOscillation ledger, RealOscillation consumer row, Real seal handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each Real or Completion-facing oscillation request through
$$
D,\mu,W,R,O,Q \longmapsto S \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\DyadicOscillationModulusUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\CauchyOscillationUp$, $\RealOscillationUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicOscillationModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,\mu,W,R,O,Q,S,H,C,P,N$ and the displayed routes among those rows. It has no coordinate for quotient stream equality, selected limits, trichotomy, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Dyadic oscillation modulus NameCert obligations]
\label{thm:dyadic-oscillation-modulus-namecert-obligations}
For every accepted $\DyadicOscillationModulusUp$ carrier
$$
M_{\mathrm{osc}}=(D,\mu,W,R,O,Q,S,H,C,P,N),
$$
the local $\NameCert_{\DyadicOscillationModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the dyadic tolerance, modulus schedule, tail window, regular rational readback, CauchyOscillation ledger, RealOscillation consumer row, Real seal handoff, transport, replay, provenance, and local naming rows;
\item modulus exposure, requiring $\mu$ to answer the tolerance request named by $D$ before $W$ or $R$ is consumed;
\item tail-window handoff, requiring $W$ and $R$ to be the only stream and regular rational rows from which $O$ is read;
\item Real boundary handoff, requiring $Q$ and $S$ to receive the same $D,\mu,W,R,O$ route before any Real or Completion-facing oscillation consumer can use the seal;
\item nonescape, requiring $H,C,P,N$ to export no quotient stream equality, selected limit, trichotomy, countable-choice schedule, host real equality, ambient Real completeness, Lean verification, bridge credential, or row outside $M_{\mathrm{osc}}$.
\end{enumerate}
No dyadic oscillation-modulus obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dyadic-oscillation-modulus-carrier}. The accepted packet displays exactly the dyadic tolerance, modulus schedule, stream window, regular rational readback, Cauchy oscillation ledger, Real oscillation consumer row, Real seal handoff, and structural rows.

The modulus exposure clause is read from $D$ and $\mu$. A consumer first names the dyadic precision request through $D$; the schedule row $\mu$ then returns a finite tail threshold for that request. No coordinate in the packet can replace this threshold by a selected infinite choice function.

The tail-window clause is supplied by $W,R,O$. The window $W$ is opened at the threshold named by $\mu$, the row $R$ repacks exactly those observations as regular rational data, and the CauchyOscillation ledger $O$ reads the tolerance $D$ over that same displayed window.

The Real boundary clause is supplied by $Q$ and $S$. The RealOscillation consumer row receives the dyadic tolerance, threshold, window, readback, and Cauchy ledger as one packet, and only then may the terminal Real seal handoff be exposed.

The structural rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since the carrier inventory omits the excluded objects, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Dyadic oscillation modulus tail handoff]
\label{thm:dyadic-oscillation-modulus-tail-handoff}
Let
$$
M_{\mathrm{osc}}=(D,\mu,W,R,O,Q,S,H,C,P,N)
$$
be an accepted $\DyadicOscillationModulusUp$ carrier. Every displayed CauchyOscillation read of $O$ factors through the finite tail route
$$
D \longmapsto \mu \longmapsto W \longmapsto R \longmapsto O .
$$
Thus the CauchyOscillation ledger receives a dyadic tolerance, a modulus-selected threshold, a finite StreamName window, and a RegSeqRat readback before it can expose tail comparisons. It cannot bypass the packet through quotient stream equality, selected limits, countable choice, or a host real comparison.
\end{theorem}
\begin{proof}
Project the accepted carrier. The row $O$ is present only as the CauchyOscillation ledger coordinate of the packet, and its available numerical inputs are the tolerance $D$, the schedule $\mu$, the window $W$, and the readback $R$.

The schedule determines the window. A read of $O$ first presents the tolerance request $D$ to $\mu$, then opens the finite StreamName window $W$ at the displayed threshold. The regular rational row $R$ is obtained from that window before the ledger can compare tail observations.

The replay row $C$ and transport row $H$ preserve this route componentwise. Provenance $P$ and the local name $N$ package the same route, so no quotient stream equality, selected limit, countable-choice schedule, or host real comparison is available as an alternate source for $O$.
\end{proof}

\begin{theorem}[Dyadic oscillation modulus Real boundary]
\label{thm:dyadic-oscillation-modulus-real-boundary}
For every accepted $\DyadicOscillationModulusUp$ carrier
$$
M_{\mathrm{osc}}=(D,\mu,W,R,O,Q,S,H,C,P,N),
$$
each Real or Completion-facing oscillation read factors through the displayed route
$$
D,\mu,W,R,O \longmapsto Q \longmapsto S \longmapsto H,C,P,N .
$$
Consequently the read reaches the $\RealOscillationUp$ consumer row $Q$ and the terminal $\RealUp$ seal handoff $S$ only after the dyadic modulus route and CauchyOscillation source ledger have been displayed. The boundary exports no quotient stream equality, selected limit, trichotomy, countable-choice schedule, host real equality, ambient Real completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Start from the carrier projection. The Real-facing rows are $Q$ and $S$, but $Q$ is specified as the consumer of the dyadic tolerance, modulus schedule, tail window, regular rational readback, and CauchyOscillation ledger, while $S$ is exposed only after that consumer row is displayed.

Apply the tail handoff theorem. Every read of $O$ already factors through $D,\mu,W,R$. Therefore any read that reaches $Q$ through $O$ carries the same dyadic tolerance request, threshold schedule, finite window, and regular rational readback.

The structural rows make the boundary exhaustive. Componentwise transport and replay preserve $D,\mu,W,R,O,Q,S$ as one finite route, and provenance plus local naming add no external equality, selected limit, trichotomy, countable-choice schedule, host real object, ambient completeness principle, Lean credential, or bridge credential.
\end{proof}

\closureat{DyadicOscillationModulusUp}{seedStr}

\begin{closurestatus}{\DyadicOscillationModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-oscillation-modulus-carrier}, \autoref{thm:dyadic-oscillation-modulus-namecert-obligations}, \autoref{thm:dyadic-oscillation-modulus-tail-handoff}, and \autoref{thm:dyadic-oscillation-modulus-real-boundary} seed the finite dyadic oscillation-modulus route from tolerance requests through modulus-selected tail windows, regular rational readback, CauchyOscillation ledgers, RealOscillation consumers, Real seal handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, trichotomy, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus exposure, tail-window handoff, Real boundary handoff, nonescape, transport, replay, provenance, and local naming for BEDC.Derived.DyadicOscillationModulusUp.}
  \constructivestory{A $\DyadicOscillationModulusUp$ packet is generated from one DyadicRatCore tolerance row, one finite modulus schedule, one StreamName tail window, one RegSeqRat readback row, one CauchyOscillation ledger, one RealOscillation consumer row, one RealUp seal handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
