\chapter{A Concrete Naming Certificate for $\RealityConstrainedOpenFitUp$}
\label{ch:concrete-instances-reality-constrained-open-fit-namecert}
\origin{ai}

The $\RealityConstrainedOpenFitUp$ packet realizes the finite-observation and open-fit discipline of \autoref{sec:finite-observation-open-fit} as a concrete BEDC NameCert carrier. It sits after the audit packet of \autoref{ch:concrete-instances-reality-constrained-model-audit-namecert}, the observation-reflection packet of \autoref{ch:concrete-instances-observationreflectionpacket-namecert}, the finite observation interface of \autoref{ch:concrete-instances-finite-observation-interface-namecert}, and the observer-budget support surface of \autoref{ch:concrete-instances-observer-budget-support-namecert}. Those siblings supply audit, reflection, finite-window, and budget rows; this carrier binds finite fit to an open continuation and a finite refutation surface without exporting a final-fit oracle.

\begin{definition}[Reality-constrained open-fit carrier]
\label{def:reality-constrained-open-fit-carrier}
A $\RealityConstrainedOpenFitUp$ carrier is a finite $\BHist$ packet
$$
U=(H,\Pi,O,M,F,Q,L,R,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $H$ is the finite trace row through which the reality-facing system is observed;
\item $\Pi$ is the observation-bundle row naming the admissible finite questions;
\item $O$ is the observed-signature row extracted from $H$ through $\Pi$;
\item $M$ is the model-signature row generated by the candidate model over the same finite trace;
\item $F$ is the finite-fit certificate row comparing $O$ and $M$ at the displayed prefix;
\item $Q$ is the open-continuation surface recording the admissible next observations still outside the finite fit row;
\item $L$ is the ledger row recording observation provenance, accepted fit, undecided continuation, and refused final-fit claims;
\item $R$ is the refutation row naming displayed defeating observations that invalidate the finite-fit certificate;
\item $N$ is the local $\NameCert_{\RealityConstrainedOpenFitUp}$ row.
\end{enumerate}
The carrier contains no coordinate for total model identity, no final-fit oracle, no host-level physical truth predicate, and no unbudgeted observation route beyond the displayed continuation and refutation rows.
\end{definition}
\leanchecked{BEDC.Derived.RealityConstrainedOpenFitUp.TasteGate.RealityConstrainedOpenFitTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Reality-constrained open-fit NameCert obligations]
\label{thm:reality-constrained-open-fit-namecert-obligations}
For the carrier of \autoref{def:reality-constrained-open-fit-carrier}, the local $\NameCert_{\RealityConstrainedOpenFitUp}$ surface consists exactly of carrier admission for $U=(H,\Pi,O,M,F,Q,L,R,N)$, signature exactness through $O$ and $M$, finite-fit exactness through $F$, open-continuation preservation through $Q$, ledger exactness through $L$, finite refutation exposure through $R$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission projects the nine displayed rows of \autoref{def:reality-constrained-open-fit-carrier}. The trace, bundle, observed signature, model signature, fit certificate, continuation surface, ledger, refutation row, and local name are the complete finite packet.

Signature and finite-fit exactness follow by reading $O$, $M$, and $F$ together. The fit row compares only the observed and model signatures available at the displayed prefix, so it cannot be detached as a total confirmation claim.

Open-continuation preservation and ledger exactness keep $Q$ and $L$ visible on every consumer route. The continuation row records the remaining observation surface, while the ledger records which fit claims, undecided continuations, and refused final-fit demands are part of the packet.

Finally the refutation row $R$ supplies the finite defeating surface. Since the carrier has no coordinate beyond $H,\Pi,O,M,F,Q,L,R,N$, local naming through $N$ cannot export model identity, a final-fit oracle, or an unbudgeted observation route.
\end{proof}

\begin{theorem}[Reality-constrained open-fit finite refutation surface]
\label{thm:reality-constrained-open-fit-finite-refutation-surface}
Every accepted $\RealityConstrainedOpenFitUp$ packet exposes refutation only through the displayed row $R$. A single defeating observation may refute the finite-fit certificate $F$ when it is recorded in $R$, but the open-continuation row $Q$ does not become a final confirmation surface when no such defeating observation has yet appeared.
\end{theorem}
\begin{proof}
Read the carrier inventory. The only row that names defeating observations is $R$, and the only row that records finite fit is $F$.

If a defeating observation is displayed in $R$, the packet has a finite witness against the corresponding fit row. This is a prefix-level refutation of $F$, not a judgment about all possible continuations.

If no defeating observation has appeared, the continuation row $Q$ remains open. It records admissible next observations still outside the finite prefix and therefore cannot certify final agreement between the model and the reality-facing system.
\end{proof}

\begin{theorem}[Reality-constrained open-fit ledger non-escape]
\label{thm:reality-constrained-open-fit-ledger-nonescape}
Every consumer of an accepted $\RealityConstrainedOpenFitUp$ packet must read finite fit through the trace $H$, bundle $\Pi$, observed signature $O$, model signature $M$, finite-fit certificate $F$, open continuation surface $Q$, ledger $L$, refutation row $R$, and local name $N$. No consumer may detach $F$ as model identity, total confirmation, a final-fit oracle, host physical truth, or an unledgered future-observation claim.
\end{theorem}
\begin{proof}
Use the NameCert obligations above. They require every accepted read to pass through the displayed signature, finite-fit, continuation, ledger, refutation, and naming rows.

The ledger row $L$ records the status of accepted finite fit, undecided continuation, and refused final-fit demands. A consumer route that omits $L$ has no place to distinguish finite support from total confirmation.

The continuation and refutation rows $Q$ and $R$ then enforce non-escape. Future observations remain open through $Q$, while finite defeat is displayed through $R$; neither row supplies model identity, host physical truth, or a final-fit oracle.
\end{proof}

The later Lean file \texttt{lean4/BEDC/Derived/RealityConstrainedOpenFitUp/TasteGate.lean} must provide explicit $\mathsf{Nontrivial}\ \RealityConstrainedOpenFitUp$ and $\mathsf{FieldFaithful}\ \RealityConstrainedOpenFitUp$ instances preserving $H,\Pi,O,M,F,Q,L,R,N$.

\falsifiablePrediction{A single displayed defeating observation refutes the finite-fit row, while no finite prefix exports a final-fit oracle.}

\independenceWitness{reality-constrained-model-audit, observationreflectionpacket, finite-observation-interface, observer-budget-support, onticstate: none is bijective because RealityConstrainedOpenFitUp stores the open-fit relation and its finite refutation surface rather than an audit packet, reflection packet, observation window, support budget, or ontic source row.}

\closureat{RealityConstrainedOpenFitUp}{seedStr}
\closureat{RealityConstrainedOpenFitUp}{obligationStr}[BEDC.Derived.RealityConstrainedOpenFitUp.TasteGate.RealityConstrainedOpenFitTasteGate\_single\_carrier\_alignment]
\closureat{RealityConstrainedOpenFitUp}{scopedStr}[BEDC.Derived.RealityConstrainedOpenFitUp.taste\_gate]

\begin{closurestatus}{\RealityConstrainedOpenFitUp}
  \constructivestory{A $\RealityConstrainedOpenFitUp$ packet is generated from a finite trace, observation bundle, observed signature, model signature, finite-fit certificate, open-continuation surface, ledger, finite refutation row, and local NameCert row.}
  \leanchecked{BEDC.Derived.RealityConstrainedOpenFitUp.taste\_gate}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:reality-constrained-open-fit-carrier}, \autoref{thm:reality-constrained-open-fit-namecert-obligations}, \autoref{thm:reality-constrained-open-fit-finite-refutation-surface}, and \autoref{thm:reality-constrained-open-fit-ledger-nonescape} bind the finite trace $H$, observation bundle $\Pi$, observed signature $O$, model signature $M$, finite-fit row $F$, continuation surface $Q$, ledger row $L$, refutation row $R$, local NameCert row $N$, TasteGate nontriviality, and field-faithfulness rows.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.RealityConstrainedOpenFitUp.TasteGate.RealityConstrainedOpenFitTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not assert model identity, total confirmation, final-fit oracles, host physical truth, public closure, or bridge checking for $\RealityConstrainedOpenFitUp$.}
  \upgradepath{Scoped closure requires binding the obligation surface to the exact trace, bundle, signature, finite-fit, continuation, ledger, refutation, and local NameCert primitive rows.}
\end{closurestatus}
