\chapter{A Concrete Naming Certificate for $\SelectionFreeCauchyRealUp$}
\label{ch:concrete-instances-selection-free-cauchy-real-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, this packet records the real-name route whose equality and seal reads pass through displayed Cauchy classifier data, not quotient streams, selected limits, countable choice, host real equality, or ambient completeness. Its dependency surface is the $\StreamNameUp$ window interface of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ regular readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the classifier row of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The chapter isolates the finite L10 handoff used by later Real and Completion consumers when the route must remain selection-free.

\begin{definition}[Selection-free Cauchy real carrier]
\label{def:real-cauchy-selection-free-carrier}
A $\SelectionFreeCauchyRealUp$ carrier is a finite $\BHist$ packet
$$
K=(S,R,D,Q,E,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ window family through which every finite observation of the Cauchy name is opened.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the dyadic bounds used by the regular readback and by Cauchy comparison requests.
\item $Q$ is the $\CauchyEquivalenceSetoidUp$ classifier row, recording equality of accepted names only through displayed Cauchy comparison data.
\item $E$ is the terminal $\RealUp$ seal reached after $S,R,D,Q$ have been displayed.
\item $B$ is the no-choice boundary, recording that the packet exports no quotient stream representative, selected limit, countable-choice schedule, host real equality, or ambient completeness witness.
\item $H$ records componentwise $\hsame$ transport for the window, readback, dyadic ledger, classifier, seal, boundary, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of every equality or seal read through
$$
S,R,D,Q,B \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\SelectionFreeCauchyRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyEquivalenceSetoidUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SelectionFreeCauchyRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,R,D,Q,E,B,H,C,P,N$.
\end{definition}

\begin{theorem}[Selection-free Cauchy real NameCert obligations]
\label{thm:real-cauchy-selection-free-namecert-obligations}
For every accepted $\SelectionFreeCauchyRealUp$ carrier
$$
K=(S,R,D,Q,E,B,H,C,P,N),
$$
the local $\NameCert_{\SelectionFreeCauchyRealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the stream windows, regular readback, dyadic tolerance ledger, Cauchy classifier, Real seal, no-choice boundary, transport, replay, provenance, and local naming rows;
\item window exactness, requiring every observation used by equality or seal reads to be one of the displayed $\StreamNameUp$ windows in $S$;
\item regular readback, requiring each rational observation consumed downstream to pass through the displayed $\RegSeqRatUp$ row $R$;
\item dyadic tolerance exactness, requiring every Cauchy comparison budget to be the displayed $\DyadicRatCoreUp$ row $D$;
\item classifier-law stability, requiring the $\CauchyEquivalenceSetoidUp$ row $Q$ to preserve reflexive, symmetric, and transitive Cauchy comparison only through $S,R,D$;
\item Real seal boundary, requiring $E$ to be read only after $S,R,D,Q$ and the no-choice boundary $B$ have been displayed;
\item no-choice refusal, requiring $B$ to exclude quotient streams, selected limits, countable choice, host real equality, and ambient completeness;
\item structural rows, requiring $H,C,P,N$ to transport, replay, source, and name exactly the displayed route.
\end{enumerate}
No selection-free Cauchy real NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-cauchy-selection-free-carrier}. The visible packet consists of the stream windows, regular readback, dyadic ledger, Cauchy classifier, Real seal, no-choice boundary, and structural rows.

Window exactness and regular readback are forced by the first two observation coordinates. A downstream read may inspect only $S$, and every rational value extracted from those windows must pass through $R$.

Dyadic tolerance exactness is the row $D$. It supplies the comparison budgets used by the Cauchy classifier and by any later seal-facing request.

Classifier-law stability is local to $Q$. The classifier may use the displayed $S,R,D$ rows to compare accepted names, but it has no coordinate for quotient stream equality or host real equality.

Finally, the Real seal boundary and the no-choice refusal are recorded by $E$ and $B$. The rows $H,C,P,N$ preserve the same route by transport, replay, provenance, and local naming, so the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Selection-free Cauchy real seal boundary]
\label{thm:real-cauchy-selection-free-seal-boundary}
Every $\RealUp$ or $\RealCompletenessUp$ consumer of an accepted $\SelectionFreeCauchyRealUp$ carrier
$$
K=(S,R,D,Q,E,B,H,C,P,N)
$$
reaches the seal row $E$ only after the stream windows $S$, regular readback $R$, dyadic tolerance ledger $D$, Cauchy classifier row $Q$, no-choice boundary $B$, transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$ have been displayed. Consequently such a consumer receives a finite Cauchy real-name route and receives no quotient stream, selected limit, countable-choice schedule, host real equality, or ambient completeness theorem from the packet.
\end{theorem}
\begin{proof}
Let a $\RealUp$ or $\RealCompletenessUp$ consumer read an accepted carrier. Projection from \autoref{def:real-cauchy-selection-free-carrier} gives only the rows $S,R,D,Q,E,B,H,C,P,N$.

The real-name route starts with the displayed windows $S$. The readback row $R$ supplies regular rational observations, and the dyadic ledger $D$ supplies the tolerance budget attached to those observations.

The equality-facing step then passes through $Q$. Its Cauchy classifier laws are read before the Real seal and only through the displayed window, readback, and dyadic rows.

The no-choice row $B$ is part of the same route before $E$ is exposed. It blocks quotient representatives, selected limits, choice schedules, host real equality, and ambient completeness witnesses from becoming seal data.

The structural rows $H,C,P,N$ transport, replay, source, and name the route without adding further mathematical coordinates. Thus every Real or Completion consumer reaches $E$ only through the displayed selection-free boundary.
\end{proof}

\closureat{SelectionFreeCauchyRealUp}{seedStr}

\begin{closurestatus}{\SelectionFreeCauchyRealUp}
  \constructivestory{A $\SelectionFreeCauchyRealUp$ packet is generated from StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a CauchyEquivalenceSetoid classifier row, a RealUp seal, a no-choice boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-cauchy-selection-free-carrier}, \autoref{thm:real-cauchy-selection-free-namecert-obligations}, and \autoref{thm:real-cauchy-selection-free-seal-boundary} seed the finite selection-free Cauchy real-name route from displayed Cauchy classifier data to the public Real seal.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.SelectionFreeCauchyRealUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, countable choice, host real equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, window exactness, regular readback, dyadic tolerance exactness, classifier-law stability, Real seal boundary, no-choice refusal, and local NameCert obligations for BEDC.Derived.SelectionFreeCauchyRealUp.}
\end{closurestatus}
