\chapter{A Concrete Naming Certificate for $\ArchimedeanBracketUp$}
\label{ch:concrete-instances-archimedean-bracket-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\ArchimedeanBracketUp$ packet records the finite integer-window route by which a displayed real name is bracketed before a Real or Completion consumer reads a located approximation. It consumes the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, the integer boundary rows of \autoref{ch:concrete-instances-int-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}. The packet gives downstream order, fractional-part, located-comparison, and approximation chapters a named bracket surface without importing host floor functions, trichotomy, quotient real equality, selected integer parts, ambient $\RealUp$ completeness, Lean verification, or bridge checking.

\begin{definition}[Archimedean bracket carrier]
\label{def:archimedean-bracket-carrier}
An $\ArchimedeanBracketUp$ carrier is a finite $\BHist$ packet
$$
B=(R,L,U,D,S,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ source row whose displayed name is being bracketed at the requested precision.
\item $L$ is the $\IntUp$ lower bracket row, recording the displayed integer bound admitted below the readback window.
\item $U$ is the $\IntUp$ upper bracket row, recording the displayed integer bound admitted above the readback window.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used to state the finite dyadic radius and comparison scale for the bracket request.
\item $S$ is the $\StreamNameUp$ finite-window row opened from $R$ at the tolerance recorded by $D$.
\item $Q$ is the $\RegSeqRatUp$ readback row that converts the displayed stream samples into rational observations before the integer rows are compared.
\item $H$ records componentwise $\hsame$ transport for the real source, lower and upper integer rows, dyadic tolerance, stream windows, regular rational readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
R,D,S,Q,L,U \longmapsto \NameCert_{\ArchimedeanBracketUp}.
$$
\item $P$ is the $\Pkg$ provenance over $\ArchimedeanBracketUp$, $\RealUp$, $\IntUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ArchimedeanBracketUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,L,U,D,S,Q,H,C,P,N$. It has no coordinate for a host floor operation, trichotomy on real values, quotient real equality, a selected integer part, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.
\end{definition}

\begin{theorem}[Archimedean bracket NameCert obligations]
\label{thm:archimedean-bracket-namecert-obligations}
For every accepted $\ArchimedeanBracketUp$ carrier
$$
B=(R,L,U,D,S,Q,H,C,P,N),
$$
the local $\NameCert_{\ArchimedeanBracketUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the Real source row, lower and upper integer bracket rows, dyadic tolerance row, stream-window row, regular rational readback row, transport, replay, provenance, and local naming row;
\item source-before-window routing, requiring $S$ to be opened only from the displayed $\RealUp$ row $R$ at the tolerance recorded by $D$;
\item readback-before-bracket routing, requiring $Q$ to expose the rational observations used by both integer comparisons before either $L$ or $U$ is exported as a bracket endpoint;
\item lower and upper endpoint exposure, requiring $L$ and $U$ to be the only integer rows visible to downstream bracket consumers;
\item transport and replay stability, requiring $H$ and $C$ to preserve the same row order without adding a second real source or another integer endpoint;
\item provenance and local naming, requiring $P$ and $N$ to source and name only the displayed packet.
\end{enumerate}
No Archimedean bracket obligation is stored outside these rows, and none exports host floor, trichotomy, quotient real equality, selected integer parts, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:archimedean-bracket-carrier}. The accepted packet displays exactly the Real source, lower and upper integer rows, dyadic tolerance, stream windows, regular rational readback, transport, replay, provenance, and local name.

The source and tolerance rows determine the finite window. The row $S$ is opened only from $R$ at the dyadic scale stored in $D$, so a bracket consumer cannot replace the displayed real-name route by a host real value.

The rational readback precedes the integer endpoints. The row $Q$ reads the displayed stream samples before $L$ and $U$ are compared with that observation, making the two integer rows bracket endpoints for the same finite window.

The structural rows preserve the route. Componentwise transport through $H$ and replay through $C$ keep $R,D,S,Q,L,U$ aligned, while $P$ and $N$ provide only provenance and local naming.

Since the excluded principles have no coordinate in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Archimedean bracket Real-window handoff]
\label{thm:archimedean-bracket-real-window-handoff}
Every accepted $\ArchimedeanBracketUp$ read exported to a Real or Completion consumer factors through the displayed finite route
$$
R \longmapsto D \longmapsto S \longmapsto Q \longmapsto (L,U) \longmapsto H,C,P,N .
$$
The consumer receives a single $\RealUp$ source row, one $\DyadicRatCoreUp$ tolerance row, one $\StreamNameUp$ window row, one $\RegSeqRatUp$ readback row, two $\IntUp$ endpoint rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row. The handoff is not a host floor theorem, not real trichotomy, not quotient real equality, not a selected integer part, not ambient $\RealUp$ completeness, and not bridge verification.
\end{theorem}
\begin{proof}
Project the accepted carrier $B=(R,L,U,D,S,Q,H,C,P,N)$. The Real-facing read begins with $R$, and the only tolerance visible to the packet is the dyadic row $D$.

Open the finite stream window $S$ at that tolerance. Its regular rational readback is the row $Q$, which supplies the finite observations against which the integer rows are displayed.

The lower and upper bracket rows are then read together. Because $L$ and $U$ are the only integer coordinates in the carrier, every downstream bracket endpoint is one of those two rows and is attached to the same readback $Q$.

Finally, $H,C,P,N$ transport, replay, source, and name the same route. No carrier coordinate can supply a host floor, trichotomy, quotient equality, selected integer part, ambient completeness theorem, or bridge credential, so every exported bracket handoff factors through the displayed finite route.
\end{proof}

\falsifiablePrediction{Every $\ArchimedeanBracketUp$ bracket read factors through one RealUp source row, one DyadicRatCore tolerance row, one StreamName finite-window row, one RegSeqRat readback row, two IntUp endpoint rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{real, int, dyadicratcore, streamname, regseqrat: $\ArchimedeanBracketUp$ is not bijective to any listed sibling because it jointly carries a Real source, a dyadic tolerance, a stream window, a regular rational readback, and lower and upper integer endpoint rows as one bracket certificate.}

\closureat{ArchimedeanBracketUp}{seedStr}

\begin{closurestatus}{\ArchimedeanBracketUp}
  \constructivestory{An $\ArchimedeanBracketUp$ packet is generated from a Real source row, lower and upper Int rows, a DyadicRatCore tolerance row, a StreamName finite-window row, a RegSeqRat readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:archimedean-bracket-carrier}, \autoref{thm:archimedean-bracket-namecert-obligations}, and \autoref{thm:archimedean-bracket-real-window-handoff} seed the finite integer-window bracket certificate over Real, dyadic tolerance, stream-window, regular rational readback, and integer endpoint rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host floor functions, trichotomy, quotient real equality, selected integer parts, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-before-window routing, readback-before-bracket routing, lower and upper endpoint exposure, transport and replay stability, provenance, and local naming for BEDC.Derived.ArchimedeanBracketUp.}
\end{closurestatus}
