\chapter{A Concrete Naming Certificate for $\ArchimedeanModulusUp$}
\label{ch:concrete-instances-archimedeanmodulus-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\ArchimedeanModulusUp$ packet records the finite precision modulus by which an explicit Archimedean bound is turned into a bounded Real-facing observation route. It sits over the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, the Real-facing modulus route of \autoref{ch:concrete-instances-realcauchymodulus-namecert}, and the explicit rational-bound surface of \autoref{ch:concrete-instances-archimedeanreal-namecert}. The packet is a bridge object for L10 Real and Completion work: it supplies a displayed bound-to-window schedule without reading host real equality, trichotomy, selected limits, quotient representatives, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Archimedean modulus carrier]
\label{def:archimedean-modulus-carrier}
An $\ArchimedeanModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(P,D,S,Q,E,A,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the unary precision request. It names the requested observation depth as finite successor data rather than as an external real-valued tolerance.
\item $D$ is the $\DyadicRatCoreUp$ bound/tolerance row. It records the dyadic comparison budget attached to the requested precision and to the displayed Archimedean bound.
\item $S$ is the $\StreamNameUp$ finite-window schedule selected by $P$ and $D$.
\item $Q$ is the $\RegSeqRatUp$ readback row inspected on the windows named by $S$.
\item $E$ is the terminal $\RealUp$ seal row reached only after $P,D,S,Q$ have been consumed.
\item $A$ is the $\ArchimedeanRealUp$ rational-bound witness attached to the same displayed real name as $E$.
\item $H$ records componentwise $\hsame$ transport for the precision request, dyadic row, finite windows, regular readback, Real seal, Archimedean witness, continuation, and local naming rows.
\item $C$ records the displayed $\Cont$ replay from each unary precision request through $P,D,S,Q,E,A,H,N$.
\item $N$ is the local $\NameCert_{\ArchimedeanModulusUp}$ row.
\end{enumerate}
The carrier has no coordinate for host real equality, trichotomy, selected limits, quotient representatives, countable choice, ambient $\RealUp$ completeness, or a hidden unbounded stream read.
\end{definition}

\begin{theorem}[Archimedean modulus NameCert obligations]
\label{thm:archimedean-modulus-namecert-obligations}
For an accepted $\ArchimedeanModulusUp$ carrier $M=(P,D,S,Q,E,A,H,C,N)$, the local $\NameCert_{\ArchimedeanModulusUp}$ surface consists exactly of carrier admission, unary precision exposure, dyadic bound/tolerance exposure, finite-window exposure, regular rational readback, Real seal exposure, Archimedean rational-bound handoff, componentwise transport, displayed continuation replay, and local naming. Each accepted precision request is classified only through the displayed route
$$
P \longmapsto D \longmapsto S \longmapsto Q \longmapsto E,A \longmapsto H,C,N .
$$
\end{theorem}
\begin{proof}
Project the carrier tuple in \autoref{def:archimedean-modulus-carrier}. Its coordinates are exactly the unary precision request, dyadic bound/tolerance row, finite-window schedule, regular readback, Real seal, Archimedean bound witness, transport, continuation, and local naming rows.

Induct over the displayed unary precision request $P$. The zero request consumes the bound/tolerance row $D$ only at the base observation depth and then names the corresponding finite window in $S$. The successor request repeats the same finite step after exposing one more unary layer, so the read never becomes an unbounded stream request.

After the window is named, the readback row $Q$ and the seal row $E$ are downstream of $D$ and $S$, while $A$ supplies only the already displayed Archimedean rational-bound witness. The rows $H,C,N$ transport, replay, and name the same route. Since none of host real equality, trichotomy, selected limits, quotient representatives, countable choice, ambient $\RealUp$ completeness, or a hidden selector has a coordinate in $M$, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Archimedean modulus window bound]
\label{thm:archimedean-modulus-window-bound}
Every accepted $\ArchimedeanModulusUp$ packet $M=(P,D,S,Q,E,A,H,C,N)$ binds each unary precision request to a finite $\StreamNameUp$ window before any $\RegSeqRatUp$ readback or $\RealUp$ seal is available. The selected window is bounded by the displayed $\DyadicRatCoreUp$ row $D$ together with the $\ArchimedeanRealUp$ witness $A$; it is not selected by real trichotomy, a host supremum, quotient representatives, countable choice, a chosen limit, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the unary request $P$. By \autoref{thm:archimedean-modulus-namecert-obligations}, every accepted read must expose $D$ before $S$, so the dyadic bound/tolerance row is available before the finite window is named.

Induct on $P$. The base request uses the first displayed tolerance row and the Archimedean witness $A$ to name the corresponding finite window. In the successor step, the previous finite route is replayed and the next tolerance row is read through the same $D,A$ surface before the next finite window is admitted.

Now inspect the downstream rows. The regular readback $Q$ and Real seal $E$ are read only after the window in $S$ is displayed, while $H,C,N$ preserve and name that route. Thus the window bound is internal to the displayed dyadic and Archimedean rows and cannot be supplied by host real equality, trichotomy, a host supremum, quotient representatives, countable choice, selected limits, or ambient Real completeness.
\end{proof}

\begin{theorem}[Archimedean modulus Real handoff]
\label{thm:archimedean-modulus-real-handoff}
Every Real-and-Completion consumer of an accepted $\ArchimedeanModulusUp$ packet factors through
$$
P \longmapsto D \longmapsto S \longmapsto Q \longmapsto E \longmapsto A \longmapsto H,C,N
$$
before reading the bounded precision-modulus surface. In particular, $\RealCauchyModulusUp$, $\RegSeqRatUp$, $\RealUp$, and bounded lower-cut consumers receive the displayed dyadic tolerance, finite-window, regular readback, Real seal, and Archimedean witness rows, and receive no host real equality, trichotomy, selected limit, quotient representative, countable-choice row, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Project the accepted packet. The Real-facing rows are $Q$ and $E$, but they are unavailable until the unary precision request $P$, dyadic row $D$, and finite-window schedule $S$ have been read.

Apply the window-bound theorem. It binds every window request to the displayed dyadic tolerance row and Archimedean rational-bound witness, so downstream consumers inherit an explicit finite modulus surface rather than a host completeness argument.

Finally replay the continuation row $C$ and transport row $H$. These rows preserve the same route for $\RealCauchyModulusUp$, $\RegSeqRatUp$, $\RealUp$, and bounded lower-cut consumers, while $N$ names the packet locally. The carrier inventory excludes host real equality, trichotomy, selected limits, quotient representatives, countable choice, and ambient $\RealUp$ completeness, so none of those sources can enter the Real handoff.
\end{proof}

\closureat{ArchimedeanModulusUp}{seedStr}

\begin{closurestatus}{\ArchimedeanModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:archimedean-modulus-carrier}, \autoref{thm:archimedean-modulus-namecert-obligations}, \autoref{thm:archimedean-modulus-window-bound}, and \autoref{thm:archimedean-modulus-real-handoff} seed the finite Archimedean precision-modulus surface from unary precision requests through dyadic tolerances, finite stream windows, regular rational readback, Real seals, Archimedean rational bounds, transport, continuation, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host real equality, trichotomy, selected limits, quotient representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, window-bound exactness, dyadic stability, RegSeqRat handoff, and Real seal nonescape for BEDC.Derived.ArchimedeanModulusUp.}
  \constructivestory{An $\ArchimedeanModulusUp$ packet is generated from a unary precision request, DyadicRatCore bound/tolerance row, StreamName finite-window schedule, RegSeqRat readback row, RealUp seal row, ArchimedeanReal rational-bound witness, componentwise hsame transport, displayed Cont replay, and a local NameCert row.}
\end{closurestatus}
