\chapter{A Concrete Naming Certificate for $\ChainConnectedMetricUp$}
\label{ch:concrete-instances-chain-connected-metric-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and the Bourbaki--Engelking topology tradition, the $\ChainConnectedMetricUp$ packet records connectedness through finite epsilon-chain witnesses rather than through host-level separation principles. It attaches the interval-facing corridor of \autoref{ch:concrete-instances-connectedinterval-namecert} to the located metric surface of \autoref{ch:concrete-instances-locatedspace-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the stream-window naming layer of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the real completion boundary of \autoref{ch:concrete-instances-real-namecert}. The certificate gives Real and Completion consumers a finite chain route while making no claim of host connectedness, quotient equality, Heine--Borel compactness, trichotomy, or open-cover compactness.

\begin{definition}[Chain-connected metric carrier]
\label{def:chain-connected-metric-carrier}
A $\ChainConnectedMetricUp$ carrier is a finite $\BHist$ packet
$$
K=(X,a,b,\epsilon,C,D,W,Q,E,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the metric source row, carrying the point classifier, distance classifier, and metric law ledgers read by the packet.
\item $a$ and $b$ are endpoint rows over $X$, with their names exposed only through the displayed source classifier.
\item $\epsilon$ is a positive dyadic radius request admitted by the $\DyadicRatCoreUp$ ledger.
\item $C=(c_0,\ldots,c_m)$ is a finite chain list, with $c_0$ transported from $a$ and $c_m$ transported from $b$.
\item $D$ is the dyadic tolerance ledger recording positivity, refinement, and link-radius comparison data for $\epsilon$ and every adjacent pair in $C$.
\item $W$ is the finite $\StreamNameUp$ window family used to inspect the endpoint and chain names.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational observations attached to distances, endpoint comparisons, and dyadic tolerances.
\item $E$ is the $\RealUp$ seal row, exposing only the Real-facing completion observation obtained after the finite dyadic chain rows have been read.
\item $H$ records componentwise $\hsame$ transport for the metric source, endpoints, dyadic radius, chain list, tolerance ledger, stream windows, rational readbacks, Real seal, replay row, provenance row, and local naming row.
\item $R$ records displayed $\Cont$ replay through
$$
X,a,b,\epsilon,C,D,W,Q \longmapsto E \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\ChainConnectedMetricUp$, $\ConnectedIntervalUp$, $\LocatedSpaceUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ChainConnectedMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,a,b,\epsilon,C,D,W,Q,E,H,R,P,N$. It has no coordinate for host connectedness, quotient equality, Heine--Borel compactness, trichotomy, open-cover compactness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Chain-connected metric NameCert obligations]
\label{thm:chain-connected-metric-namecert-obligations}
For every accepted $\ChainConnectedMetricUp$ carrier
$$
K=(X,a,b,\epsilon,C,D,W,Q,E,H,R,P,N),
$$
the local $\NameCert_{\ChainConnectedMetricUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the metric source, endpoints, dyadic radius, finite chain list, dyadic tolerance ledger, stream windows, regular rational readback, Real seal, transport, replay, provenance, and local naming row;
\item link-radius exactness, requiring every adjacent pair in $C$ to have its distance comparison read through $X$, $D$, and $Q$ before the link is admitted;
\item endpoint transport, requiring $c_0$ and $c_m$ to be the displayed $\hsame$ transports of $a$ and $b$ along the same packet route;
\item chain concatenation stability, requiring compatible endpoint transport and dyadic ledgers to compose by finite list concatenation without creating a second metric source;
\item Real seal nonescape, requiring $E$ to be read only after $X,a,b,\epsilon,C,D,W,Q$ have been displayed;
\item ledger refusal, rejecting any consumer that asks the packet for host connectedness, quotient equality, Heine--Borel compactness, trichotomy, open-cover compactness, Lean verification, or bridge checking.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:chain-connected-metric-carrier}. The accepted packet displays the source $X$, endpoints $a,b$, dyadic radius $\epsilon$, chain list $C$, dyadic ledger $D$, stream windows $W$, rational readback $Q$, Real seal $E$, and structural rows.

Link-radius exactness is rowwise. Each adjacent pair of the finite list $C$ is inspected through the metric source $X$, and its dyadic comparison is recorded by $D$ and read back through $Q$ before the link can contribute to the certificate.

Endpoint transport uses the same componentwise $\hsame$ row $H$ that transports the rest of the packet. Thus the first and last chain entries are tied to $a$ and $b$ without introducing an ambient equality principle.

Concatenation stability is finite list bookkeeping. Two accepted chains with matching transported endpoint rows concatenate by joining their displayed chain lists and ledgers, while the source row $X$ and the replay route remain unchanged.

The Real seal is downstream of the finite rows. Since $E$ appears only after $X,a,b,\epsilon,C,D,W,Q$ in the replay route, a Real-facing consumer cannot bypass the dyadic chain witnesses.

Finally, the classifier has no coordinates for the excluded principles. Any request for host connectedness, quotient equality, Heine--Borel compactness, trichotomy, open-cover compactness, Lean verification, or bridge checking therefore has no row to read and is refused by the local ledger.
\end{proof}

\begin{theorem}[Chain-connected metric Real completion boundary]
\label{thm:chain-connected-metric-real-completion-boundary}
Every Real-facing chain-connectedness consumer of an accepted $\ChainConnectedMetricUp$ carrier factors through the finite route
$$
X,a,b,\epsilon,C,D,W,Q \longmapsto E \longmapsto H,R,P,N
$$
before reading the $\RealUp$ seal. Consequently the packet exports only dyadic chain rows and their transported Real readback, not a host connectedness theorem, quotient equality principle, Heine--Borel compactness result, trichotomy decision, or open-cover compactness claim.
\end{theorem}
\begin{proof}
Let $K=(X,a,b,\epsilon,C,D,W,Q,E,H,R,P,N)$ be accepted. A Real-facing consumer first reads the metric source and endpoints because the chain entries and endpoint transports are meaningful only relative to the displayed source classifier.

The positive radius and finite chain are then inspected through $\epsilon$ and $C$. Every adjacent link is certified by the dyadic ledger $D$, the stream windows $W$, and the rational readback $Q$.

Only after those finite rows have been displayed does the replay route expose the Real seal $E$. The transport, replay, provenance, and local naming rows then preserve the same dependency order.

Thus each Real-facing chain-connectedness claim factors through the displayed dyadic chain route before it can read $\RealUp$. The packet has no remaining coordinate from which the excluded host-level principles could be exported.
\end{proof}

\closureat{ChainConnectedMetricUp}{seedStr}

\begin{closurestatus}{\ChainConnectedMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:chain-connected-metric-carrier}, \autoref{thm:chain-connected-metric-namecert-obligations}, and \autoref{thm:chain-connected-metric-real-completion-boundary} seed the finite epsilon-chain connectedness package over displayed metric, endpoint, dyadic tolerance, chain-list, stream-window, regular rational, Real seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host connectedness, quotient equality, Heine--Borel compactness, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, link-radius exactness, endpoint transport, chain concatenation stability, Real seal nonescape, ledger refusal, and Real completion boundary factorization for BEDC.Derived.ChainConnectedMetricUp.}
  \constructivestory{A $\ChainConnectedMetricUp$ packet is generated from a metric source row, endpoint rows, a dyadic radius, a finite chain list, a DyadicRatCore tolerance ledger, StreamName windows, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
