\chapter{A Concrete Naming Certificate for $\FirstCountableSpaceUp$}
\label{ch:concrete-instances-first-countable-space-namecert}
\origin{human}

Following Bourbaki and Kelley on countability axioms in topology, the $\FirstCountableSpaceUp$ packet records the local countable-neighbourhood interface needed between generated-open topology data and metric-completion consumers. It sits over the generated-open classifier of \autoref{ch:concrete-instances-topology-namecert}, the metric-ball basis route of \autoref{ch:concrete-instances-metric-topology-namecert}, the countable-base surface of \autoref{ch:concrete-instances-second-countable-namecert}, and the complete-separable metric consumer route of \autoref{ch:concrete-instances-polishspace-namecert}. The packet names only displayed point windows, local neighbourhood-base rows, refinement rows, radius ledgers, transport, replay, provenance, and local naming; it does not select neighbourhood bases by choice, assert open-cover compactness, identify quotient points, or import ambient $\RealUp$ completeness.

\begin{definition}[First-countable-space carrier]
\label{def:first-countable-space-carrier}
A $\FirstCountableSpaceUp$ carrier is a finite $\BHist$ packet
$$
F=(X,T,M,L,D,S,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the point or source carrier row whose finite histories are the only points inspected by the packet.
\item $T$ is the $\TopologyUp$ generated-open classifier row; every open-neighbourhood read passes through this row before it reaches a consumer.
\item $M$ is the $\MetricTopologyUp$ or metric-ball basis route when the local base is metric-presented; if no metric route is displayed, $M$ is the explicit empty witness row.
\item $L$ is the local countable-neighbourhood ledger, recording for each accepted point-window the finite index windows and neighbourhood cells exposed at that point.
\item $D$ is the dyadic radius and precision ledger used by metric-presented neighbourhood cells and completion-facing boundary reads.
\item $S$ is the $\StreamNameUp$ row for finite inspection of the local countable schedule at a displayed point-window.
\item $R$ is the $\RealUp$ boundary and seal row used only when a radius, metric-topology, or completion-facing read requires a real-valued boundary.
\item $H$ stores componentwise $\hsame$ transport for the source, topology classifier, optional metric-topology route, local schedule, dyadic ledger, stream windows, real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a point-window through the topology classifier, local schedule, optional metric route, precision ledger, stream window, real seal, transport, provenance, and local name.
\item $P$ is the $\Pkg$ provenance row over $\FirstCountableSpaceUp$, $\TopologyUp$, $\MetricTopologyUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FirstCountableSpaceUp}$ row.
\end{enumerate}
The carrier exports a displayed local countable base at each accepted point-window. It has no coordinate for a host family of all neighbourhoods, a choice-selected basis, quotient point equality, arbitrary open covers, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[First-countable-space NameCert obligations]
\label{thm:first-countable-space-namecert-obligations}
For an accepted $\FirstCountableSpaceUp$ carrier
$$
F=(X,T,M,L,D,S,R,H,C,P,N),
$$
the local $\NameCert_{\FirstCountableSpaceUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the point or source row, topology classifier, optional metric-topology route, local countable-neighbourhood ledger, dyadic ledger, stream windows, real seal, transport, replay, provenance, and local name;
\item pointwise local-basis coverage, requiring every accepted point-window and generated-open neighbourhood read to meet a displayed neighbourhood cell from $L$ through the same source row $X$ and topology row $T$;
\item pointwise refinement closure, requiring any two displayed local neighbourhood cells accepted at the same point-window to refine through another displayed local cell indexed by the same ledger $L$;
\item metric-topology handoff, requiring every metric-presented local cell to pass through $M,D,S,R$ before it is exported to a completion-facing consumer;
\item ledger nonescape, requiring every point, open-neighbourhood, radius, stream-window, real-boundary, transport, replay, provenance, and local-naming read to remain inside $X,T,M,L,D,S,R,H,C,P,N$.
\end{enumerate}
No first-countability obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:first-countable-space-carrier}. The accepted packet displays one source row, one topology classifier, one optional metric-topology route, one local countable-neighbourhood ledger, and the structural rows needed to replay and name the packet.

Pointwise local-basis coverage is read from $X,T,L$. A consumer opens a point-window in $X$, reads a generated-open neighbourhood through $T$, and receives only a displayed local cell from $L$ at the same finite point-window.

Pointwise refinement is also internal to $L$. When two local cells are accepted at one point-window, the refinement witness is another displayed entry of the same local ledger, not a selected neighbourhood from a host family.

Metric-presented cells use the route through $M,D,S,R$. The optional metric-topology row supplies the ball-basis handoff, the dyadic ledger supplies the radius precision, the stream row supplies the finite inspection window, and the real row supplies only the boundary seal requested by the consumer.

Finally $H,C,P,N$ transport, replay, source, and name the displayed rows. Since the packet contains no host neighbourhood family, choice-selected local base, quotient point equality, open-cover compactness proof, or ambient $\RealUp$ completeness field, the listed obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[First-countable to second-countable handoff]
\label{thm:first-countable-space-second-countable-handoff}
Every accepted $\SecondCountableUp$ packet induces a $\FirstCountableSpaceUp$ read by restricting the displayed countable-base enumeration to the accepted point-window. The induced first-countable read uses the same source row, topology classifier, optional metric witness, dyadic ledger, stream windows, real seal, componentwise transport, replay, provenance, and local name; only the global base enumeration is read pointwise as the local ledger $L$.
\end{theorem}
\begin{proof}
Start with the accepted $\SecondCountableUp$ carrier. Its source row, topology classifier, optional metric witness, dyadic ledger, stream row, real seal, transport, replay, provenance, and local name already have the same BEDC roles required by \autoref{def:first-countable-space-carrier}.

At a displayed point-window, read the second-countable base enumeration through its stream schedule. The local ledger $L$ is the finite list of displayed basic cells from that enumeration that are witnessed at the same point-window.

Coverage and refinement are inherited pointwise. A generated-open neighbourhood first receives a displayed basic cell from the second-countable coverage row, and two such cells refine through the second-countable refinement row before being re-read as local entries of $L$.

The remaining rows are unchanged. No selected global basis, host open family, countable-choice principle, quotient point equality, open-cover compactness theorem, or ambient $\RealUp$ completeness field is introduced by the pointwise restriction.
\end{proof}

\begin{theorem}[First-countable-space nonescape]
\label{thm:first-countable-space-nonescape}
Let $F=(X,T,M,L,D,S,R,H,C,P,N)$ be an accepted $\FirstCountableSpaceUp$ carrier. Any topology, metric-topology, completion-facing, or Polish-space consumer read of the local countable-neighbourhood surface factors through the displayed route
$$
X,T,M,L,D,S,R,H,C,P,N
$$
before it exports a neighbourhood, radius, stream window, or boundary seal. Consequently the packet cannot export open-cover compactness, a choice-selected neighbourhood basis, quotient point equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a topology consumer. It has no open-neighbourhood coordinate except $T$, and no local countable-neighbourhood coordinate except $L$, so the read starts at the source row $X$, passes through the topology classifier $T$, and then through the displayed local ledger $L$.

A metric-topology or completion-facing consumer additionally reads the optional metric route $M$. Radius and precision requests must pass through $D$, finite schedule requests through $S$, and real-boundary requests through $R$ before the consumer can observe a local cell.

The structural rows keep the same route fixed under transport and replay. Componentwise transport is recorded in $H$, replay in $C$, provenance in $P$, and local naming in $N$.

No other coordinate is available. Since the carrier omits arbitrary open covers, selected neighbourhood bases, quotient point representatives, and ambient real-completeness fields, every exported read remains inside the displayed packet.
\end{proof}

\closureat{FirstCountableSpaceUp}{seedStr}

\begin{closurestatus}{\FirstCountableSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:first-countable-space-carrier}, \autoref{thm:first-countable-space-namecert-obligations}, \autoref{thm:first-countable-space-second-countable-handoff}, and \autoref{thm:first-countable-space-nonescape} seed the local countable-neighbourhood interface over displayed source rows, topology classifiers, optional metric-topology routes, local schedules, dyadic ledgers, stream windows, real seals, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.FirstCountableSpaceUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected neighbourhood bases by choice, quotient point equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, pointwise local-basis coverage, pointwise refinement, second-countable handoff, metric-topology handoff, nonescape, transport, replay, provenance, and local naming for BEDC.Derived.FirstCountableSpaceUp.}
  \constructivestory{A $\FirstCountableSpaceUp$ packet is generated from one point or source carrier row, one Topology classifier row, an optional MetricTopology route, one local countable-neighbourhood ledger, one DyadicRatCore precision ledger, one StreamName finite-inspection row, one Real boundary row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
