\chapter{A Concrete Naming Certificate for $\EulerMaclaurinUp$}
\label{ch:concrete-instances-euler-maclaurin-namecert}
\origin{human}

Following Euler and Maclaurin, and in the Bishop--Bridges constructive reading, the $\EulerMaclaurinUp$ packet records the finite summation-remainder boundary where a displayed finite partial-sum source is compared with endpoint data, derivative-window rows, Bernoulli-style coefficients, and a dyadic remainder budget before a terminal $\RealUp$ seal is named. It sits beside the summation-by-parts route of \autoref{ch:concrete-instances-abel-summation-namecert}, the finite term and partial-sum surface of \autoref{ch:concrete-instances-realseries-namecert}, the derivative packet of \autoref{ch:concrete-instances-derivative-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only the finite BEDC route from inspected terms to a certified remainder budget; it does not import host infinite summation, host integration, selected limits, quotient equality, countable choice, trichotomy, or ambient real completeness.

\begin{definition}[Euler--Maclaurin carrier]
\label{def:euler-maclaurin-carrier}
An $\EulerMaclaurinUp$ carrier is a finite $\BHist$ packet
$$
E=(S,A,L,U,D,B,Q,R,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\RealSeriesUp$ or finite partial-sum source row, carrying the inspected term windows, finite summation bounds, and the partial-sum observations that are allowed to enter the formula.
\item $A$ is the Abel-summation comparison row, used only as a finite summation-by-parts route for rearranging the inspected partial sums.
\item $L$ and $U$ are endpoint $\RealUp$ rows for the lower and upper summation endpoints, including the endpoint readback names consumed by the boundary terms.
\item $D$ is the derivative-window row, listing the finitely inspected $\DerivativeUp$ observations and the interval windows on which the remainder estimate is read.
\item $B$ is the Bernoulli-style coefficient ledger. It records only the finite coefficient rows requested by the displayed order of the formula.
\item $Q$ is the $\DyadicRatCoreUp$ remainder-budget row, with positivity, refinement, and split-budget data for the final error request.
\item $R$ is the $\RegSeqRatUp$ readback row that exposes rational approximants for the finite sums, endpoint rows, derivative windows, coefficient ledger, and remainder budget.
\item $Z$ is the terminal $\RealUp$ seal for the finite summation-with-remainder read after $S,A,L,U,D,B,Q,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the series or finite partial-sum source, Abel row, endpoint rows, derivative windows, coefficient ledger, dyadic budget, regular rational readback, terminal real seal, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay through
$$
S,A,L,U,D,B,Q,R \longmapsto Z \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\EulerMaclaurinUp$, $\RealSeriesUp$, $\AbelSummationUp$, $\DerivativeUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\EulerMaclaurinUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,A,L,U,D,B,Q,R,Z,H,C,P,N$. It has no coordinate for a host infinite sum, host integral, selected limit, quotient equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Euler--Maclaurin NameCert obligations]
\label{thm:euler-maclaurin-namecert-obligations}
For every accepted $\EulerMaclaurinUp$ carrier
$$
E=(S,A,L,U,D,B,Q,R,Z,H,C,P,N),
$$
the local $\NameCert_{\EulerMaclaurinUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the finite series or partial-sum source, Abel row, lower and upper endpoint rows, derivative windows, coefficient ledger, dyadic remainder budget, regular rational readback, terminal real seal, transport, replay, provenance, and local naming row;
\item summation-window exposure, requiring every formula request to display the finite term windows and partial-sum bounds in $S$ before the Abel row $A$ is read;
\item endpoint readiness, requiring both endpoint $\RealUp$ rows $L,U$ to be opened before any boundary term is named;
\item derivative and coefficient readiness, requiring the derivative windows $D$ and the finite Bernoulli-style coefficient ledger $B$ to be displayed before the remainder row is accepted;
\item dyadic remainder routing, requiring the final remainder request to factor through the $\DyadicRatCoreUp$ positivity, refinement, and split-budget rows in $Q$;
\item rational readback and Real seal handoff, requiring $R$ to expose all finite rational approximants before the terminal $\RealUp$ seal $Z$ is named;
\item classifier transport, requiring $H$ and $C$ to preserve the same $S,A,L,U,D,B,Q,R,Z$ inventory under $\hsame$ and displayed $\Cont$ replay;
\item non-escape, requiring $P$ and $N$ to source and name only the listed route, with no hidden host infinite sum, host integral, selected limit, quotient equality, countable choice, trichotomy, ambient real completeness, Lean verification, or bridge checking.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:euler-maclaurin-carrier}. The accepted packet displays the finite source $S$, Abel row $A$, endpoint rows $L,U$, derivative windows $D$, coefficient ledger $B$, dyadic budget $Q$, readback row $R$, terminal seal $Z$, and structural rows $H,C,P,N$.

The summation-window and endpoint obligations are forced by row order. A formula request enters through the finite term and partial-sum source $S$, may use $A$ only as the displayed summation-by-parts route, and reads the endpoint rows $L,U$ before any boundary term is exposed.

The derivative and coefficient obligations are likewise rowwise. The window row $D$ lists the derivative observations that can participate in the remainder estimate, while $B$ lists only the finitely requested coefficient rows.

The dyadic remainder obligation comes from $Q$. Its positivity, refinement, and split-budget data are displayed before the terminal estimate is transported to the regular rational readback row $R$ and the real seal $Z$.

Finally, $H$ and $C$ replay the same inventory under classifier transport, and $P,N$ source and name only that inventory. Since the carrier has no additional coordinate, no unlisted host-analytic or choice-based obligation can be read from the packet.
\end{proof}

\begin{theorem}[Euler--Maclaurin remainder handoff]
\label{thm:euler-maclaurin-remainder-handoff}
Every remainder read exported by an accepted $\EulerMaclaurinUp$ carrier factors through the displayed route
$$
\RealSeriesUp,\AbelSummationUp,\RealUp,\DerivativeUp,\DyadicRatCoreUp,\RegSeqRatUp \longmapsto \RealUp .
$$
Equivalently, the terminal real seal $Z$ can be opened only after the finite source $S$, Abel row $A$, endpoint rows $L,U$, derivative windows $D$, coefficient ledger $B$, dyadic budget $Q$, and regular rational readback row $R$ have all been displayed.
\end{theorem}
\begin{proof}
Let $E=(S,A,L,U,D,B,Q,R,Z,H,C,P,N)$ be accepted. A remainder consumer begins with the finite formula request, so the first visible data are the term windows and partial-sum bounds in $S$.

The route may then pass through $A$ to express the finite summation-by-parts comparison. The endpoint rows $L,U$ supply the boundary-term seals, while $D$ and $B$ supply the derivative observations and coefficient rows that make the finite correction terms inspectable.

The actual remainder budget is not read until $Q$ is displayed. This dyadic row fixes the positive tolerance, refinements, and budget splits used by the later rational approximants.

The readback row $R$ then exposes rational approximants for each already displayed component, and only afterward does the terminal seal $Z$ become visible. The structural rows $H,C,P,N$ transport and name the same route, so every exported remainder read has the stated factorization.
\end{proof}

\begin{theorem}[Euler--Maclaurin Real seal non-escape]
\label{thm:euler-maclaurin-real-seal-nonescape}
For every accepted $\EulerMaclaurinUp$ carrier, any $\RealUp$ seal read produced by the packet is either one of the displayed endpoint rows $L,U$ or the terminal seal $Z$ reached through the finite route of \autoref{thm:euler-maclaurin-remainder-handoff}. No accepted carrier exports a separate $\RealUp$ seal through host integration, host infinite summation, selected limits, quotient equality, countable choice, trichotomy, ambient real completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Project an accepted carrier $E=(S,A,L,U,D,B,Q,R,Z,H,C,P,N)$. The only rows whose declared target is $\RealUp$ are the endpoint rows $L,U$ and the terminal seal $Z$.

The endpoint rows are already displayed as part of the carrier. They are not computed by a host integral or an infinite summation principle; they are named endpoint seals consumed by the finite boundary-term route.

For the terminal seal, apply \autoref{thm:euler-maclaurin-remainder-handoff}. The seal $Z$ is downstream of $S,A,L,U,D,B,Q,R$ and is therefore reached only after the finite source, boundary, derivative, coefficient, dyadic, and readback rows are visible.

The transport, replay, provenance, and naming rows do not add new real-valued coordinates. Hence there is no remaining path by which a consumer could obtain a detached real seal from an excluded host-analytic or choice-based source.
\end{proof}

\closureat{EulerMaclaurinUp}{seedStr}

\begin{closurestatus}{\EulerMaclaurinUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:euler-maclaurin-carrier}, \autoref{thm:euler-maclaurin-namecert-obligations}, \autoref{thm:euler-maclaurin-remainder-handoff}, and \autoref{thm:euler-maclaurin-real-seal-nonescape} seed the finite Euler--Maclaurin summation-remainder packet over displayed series or finite partial-sum source, Abel row, endpoint RealUp rows, derivative windows, coefficient ledger, dyadic remainder budget, regular rational readback, terminal RealUp seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, host integrals, selected limits, quotient equality, countable choice, trichotomy, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, summation-window exposure, endpoint readiness, derivative and coefficient readiness, dyadic remainder routing, rational readback, Real seal handoff, classifier transport, remainder factorization, and non-escape for BEDC.Derived.EulerMaclaurinUp.}
  \constructivestory{An $\EulerMaclaurinUp$ packet is generated from a finite RealSeries or partial-sum source row, Abel summation row, endpoint RealUp rows, derivative-window rows, a Bernoulli-style coefficient ledger, a DyadicRatCore remainder budget, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
