\chapter{A Concrete Naming Certificate for $\CertifiedPhysicalTruthUp$}
\label{ch:concrete-instances-certified-physical-truth-namecert}
\origin{ai}

The $\CertifiedPhysicalTruthUp$ packet realizes the physical-truth decomposition of \autoref{ch:visions-reality-constrained-approximation-towers} as a finite BEDC NameCert carrier. It consumes the tower packet of \autoref{ch:concrete-instances-realityconstrainedtowerpacket-namecert}, the reality-constrained approximation carrier of \autoref{ch:concrete-instances-reality-constrained-approximation-tower-namecert}, the observation-reflection packet of \autoref{ch:concrete-instances-observationreflectionpacket-namecert}, the physical-model audit surface of \autoref{ch:concrete-instances-physical-model-audit-namecert}, and the open-fit surface of \autoref{ch:concrete-instances-reality-constrained-open-fit-namecert}. Those siblings supply source access, signature comparison, approximation, handoff, audit, and refutation rows; this packet binds them into a single truth-certificate surface without adding model--reality identity or a final-fit oracle.

\begin{definition}[CertifiedPhysicalTruth carrier]
\label{def:certified-physical-truth-carrier}
A $\CertifiedPhysicalTruthUp$ carrier is a finite $\BHist$ packet
$$
T=(S,G,K,A,D,I,L,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source-observation row, recording the finite reality-facing traces or experiments admitted by the packet.
\item $G$ is the reality-facing signature row extracted from $S$ through the declared observation bundle.
\item $K$ is the classifier row comparing the displayed signature with the candidate physical claim at the stated fit level.
\item $A$ is the approximation-tower row through which mathematical approximation, completion, and prediction are read.
\item $D$ is the descent-certificate row licensing exactly the operations that survive passage through $A$.
\item $I$ is the observer-invariance certificate row, recording the displayed anchor-change or inter-observer route by which the claim remains invariant.
\item $L$ is the ledger row for provenance, compression, idealization, translation, reuse domain, and accepted evidential strength.
\item $F$ is the failure-surface row naming finite defeating observations, signature mismatches, and open residues.
\item $H$ records componentwise $\hsame$ transport for source, signature, classifier, tower, descent, invariance, ledger, failure, replay, provenance, and local-name rows.
\item $C$ records displayed $\Cont$ replay through $S,G,K,A,D,I,L,F,H,P,N$.
\item $P$ is the $\Pkg$ provenance over \autoref{ch:visions-reality-constrained-approximation-towers}, the cited concrete-instance siblings, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CertifiedPhysicalTruthUp}$ row.
\end{enumerate}
The carrier has no coordinate for host-level truth, model--reality identity, unbounded observation, unledgered approximation, privileged observer access, or final physical fit outside the displayed packet.
\end{definition}

\begin{definition}[CertifiedPhysicalTruth obligation surface]
\label{def:certified-physical-truth-obligation-surface}
For the carrier of \autoref{def:certified-physical-truth-carrier}, the local $\NameCert_{\CertifiedPhysicalTruthUp}$ surface consists exactly of eight obligation rows:
\begin{enumerate}
\item source admission through $S$;
\item reality-facing signature admission through $G$;
\item classifier exactness through $K$;
\item approximation-tower accountability through $A$;
\item descent permission through $D$;
\item observer-invariance display through $I$;
\item ledger exactness through $L$;
\item failure-surface exposure through $F$.
\end{enumerate}
The structural rows $H,C,P,N$ preserve, replay, source, and locally name those eight obligations, but they do not add another truth coordinate.
\end{definition}

\begin{theorem}[CertifiedPhysicalTruth reality fit]
\label{thm:certified-physical-truth-reality-fit}
Every accepted $\CertifiedPhysicalTruthUp$ truth read factors through the source row $S$, signature row $G$, classifier row $K$, approximation tower $A$, descent certificate $D$, observer-invariance row $I$, ledger $L$, failure surface $F$, componentwise transport $H$, replay row $C$, provenance $P$, and local name $N$. In particular, physical truth through this packet is certified fit with displayed stability, descent, invariance, ledger, and failure data, not identity between a model and reality.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:certified-physical-truth-carrier}. The accepted packet displays exactly the rows
$$
S,G,K,A,D,I,L,F,H,C,P,N.
$$

The source and signature rows $S,G$ provide the reality-facing input, while $K$ records the finite classifier comparison. The approximation row $A$ and descent row $D$ then state which mathematical operations survive the tower rather than converting the tower into physical identity.

The invariance, ledger, and failure rows $I,L,F$ supply the remaining truth-certificate constraints. The structural rows $H,C,P,N$ transport, replay, source, and name the same packet. Since no further carrier coordinate is available, every accepted truth read must remain inside the displayed fit, stability, descent, invariance, ledger, and failure surface.
\end{proof}

\begin{theorem}[CertifiedPhysicalTruth failure surface]
\label{thm:certified-physical-truth-failure-surface}
An accepted $\CertifiedPhysicalTruthUp$ packet must expose a displayed failure-surface row $F$. If a physical-truth claim asserts model--reality identity, or if the packet lacks a row naming finite defeating observations, signature mismatches, and open residues, then the claim is not accepted by $\NameCert_{\CertifiedPhysicalTruthUp}$.
\end{theorem}
\begin{proof}
Use \autoref{def:certified-physical-truth-obligation-surface}. Failure-surface exposure through $F$ is one of the eight local NameCert obligations, so a packet without $F$ lacks a required certificate row.

The same obligation surface separates the classifier $K$ and tower $A$ from any identity claim. They record finite fit and approximation accountability, while $F$ records how the claim can be defeated. A model--reality identity assertion therefore asks the carrier to export a coordinate that the packet does not contain.

Consequently the accepted packet can certify only the displayed physical-truth surface. Removing $F$ or replacing finite fit by identity leaves the local NameCert carrier.
\end{proof}

\begin{theorem}[CertifiedPhysicalTruth observer invariance]
\label{thm:certified-physical-truth-observer-invariance}
Every $\CertifiedPhysicalTruthUp$ export is invariant only through the displayed row $I$ and its componentwise transport in $H$. A truth read depending on one observer history without the invariant route recorded in $I$ is local observation content, not a certified physical-truth export.
\end{theorem}
\begin{proof}
Read the carrier fields for invariance. The only row that records observer-invariance data is $I$, and the only transport row preserving it componentwise is $H$.

The replay and provenance rows $C$ and $P$ do not introduce a privileged observer. They only replay and source the packet already transported through $H$.

Thus an accepted export must pass through $I$ before being read as observer-invariant. If the claimed truth depends on a single observer history outside that route, the claim may remain a local finite observation, but it is not exported by $\CertifiedPhysicalTruthUp$.
\end{proof}

\falsifiablePrediction{If a CertifiedPhysicalTruthUp packet asserts model--reality identity or lacks a displayed failure-surface row, the packet is refuted.}

\independenceWitness{realityconstrainedtowerpacket, realityconstrainedapproximationtower, observationreflectionpacket, physicalmodelaudit, realityconstrainedopenfit: each sibling supplies part of fit, signature, tower, handoff, audit, or refutation data, while none contains the full source, signature, classifier, tower, descent, invariant, ledger, failure-surface, transport, replay, provenance, and local NameCert truth-certificate packet.}

The Lean follow-up must provide \texttt{Nontrivial CertifiedPhysicalTruthUp} and \texttt{FieldFaithful CertifiedPhysicalTruthUp} instances in \texttt{lean4/BEDC/Derived/CertifiedPhysicalTruthUp/TasteGate.lean}.

\closureat{CertifiedPhysicalTruthUp}{seedStr}

\begin{closurestatus}{\CertifiedPhysicalTruthUp}
  \constructivestory{A $\CertifiedPhysicalTruthUp$ packet is generated from finite source observations, a reality-facing signature, classifier, approximation tower, descent certificate, observer-invariance certificate, ledger, failure surface, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:certified-physical-truth-carrier}, \autoref{def:certified-physical-truth-obligation-surface}, \autoref{thm:certified-physical-truth-reality-fit}, \autoref{thm:certified-physical-truth-failure-surface}, and \autoref{thm:certified-physical-truth-observer-invariance} bind certified physical truth to finite fit, stability, descent, observer invariance, ledger, and failure-surface rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not assert model--reality identity, host-level truth, final physical fit, unbounded observation, Lean verification, or bridge checking for $\CertifiedPhysicalTruthUp$.}
  \upgradepath{Obligation closure requires Lean encoding of the carrier, NameCert obligation surface, reality-fit theorem, failure-surface theorem, observer-invariance theorem, TasteGate nontriviality, and field faithfulness for $S,G,K,A,D,I,L,F,H,C,P,N$.}
\end{closurestatus}
