\chapter{A Concrete Naming Certificate for $\InverseFunctionUp$}
\label{ch:concrete-instances-inverse-function-namecert}
\origin{human}

Following the local inverse function theory of Cartan and Rudin, the $\InverseFunctionUp$ packet records only the finite local-inversion rows that a BEDC consumer may inspect after a displayed derivative row, an invertible linear approximation, Newton data, and the regular Cauchy real route have been opened. It consumes the local-solution boundary of \autoref{ch:concrete-instances-implicitfunction-namecert}, the Newton--Kantorovich route of \autoref{ch:concrete-instances-newton-kantorovich-namecert}, the finite step discipline of \autoref{ch:concrete-instances-newtoniteration-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names a local certificate route from displayed analytic data to a local bijection window; it does not assert a host inverse function, identify quotient function spaces, select a germ, import ambient Real completeness, or provide bridge verification.

\begin{definition}[Inverse function carrier]\label{def:inverse-function-carrier}
An $\InverseFunctionUp$ carrier is a finite $\BHist$ packet
$$
V=(F,B,D,L,K,I,J,S,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the displayed function row, recording the finite graph reads and local classifier for the source and target windows.
\item $B$ is the base-point and window row. It records the displayed point $x_0$, the displayed value $y_0$, and the source and target neighbourhood names in which the local inverse is read.
\item $D$ is the derivative row at the base point and along the displayed window.
\item $L$ is the invertible linear approximation row attached to $D$, together with the finite inverse-witness ledger used for the local inversion estimate.
\item $K$ is the $\NewtonKantorovichUp$ row that records the contraction neighbourhood and root-boundary handoff for solving $F(x)=y$ near $y_0$.
\item $I$ is the $\ImplicitFunctionUp$ row that repacks the same local solving data as a graph-window certificate for the equation $F(x)-y=0$.
\item $J$ is the finite $\NewtonIterationUp$ step ledger used by $K$ and $I$ before the endpoint is sealed.
\item $S$ is the finite $\StreamNameUp$ window row opened for source, target, and endpoint observations.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational approximations obtained from $S$.
\item $R$ is the terminal $\RealUp$ seal row reached only after the displayed analytic, Newton, implicit, stream, and regular-rational rows have been opened.
\item $H$ records componentwise $\hsame$ transport for the function row, base-point row, derivative row, invertible approximation row, Newton--Kantorovich row, implicit-function row, Newton-iteration ledger, stream windows, regular rational readback, Real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay through
$$
F,B,D,L,J,K,I,S,Q,R \longmapsto \NameCert_{\InverseFunctionUp}.
$$
\item $P$ is the $\Pkg$ provenance over $\InverseFunctionUp$, $\ImplicitFunctionUp$, $\NewtonKantorovichUp$, $\NewtonIterationUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\InverseFunctionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,B,D,L,K,I,J,S,Q,R,H,C,P,N$. The carrier has no coordinate for a host inverse function, quotient function space equality, selected inverse germ, global bijection theorem, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Inverse function NameCert obligations]\label{thm:inverse-function-namecert-obligations}
For every accepted $\InverseFunctionUp$ carrier
$$
V=(F,B,D,L,K,I,J,S,Q,R,H,C,P,N),
$$
the local $\NameCert_{\InverseFunctionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed function row, base-point and window row, derivative row, invertible approximation row, Newton--Kantorovich row, implicit-function row, Newton-iteration ledger, stream windows, regular rational readback, Real seal, transport, replay, provenance, and local name;
\item derivative and inverse-witness compatibility, requiring $D$ and $L$ to display the same local linear approximation and inverse ledger used by the solving route;
\item Newton route compatibility, requiring $J$ to be the finite step ledger read by $K$ before the root boundary is sealed;
\item implicit-function handoff, requiring $I$ to read the same local equation row and graph-window data as the Newton route rather than a second solution source;
\item L10 completion-route handoff, requiring $S,Q,R$ to be opened in order through finite StreamName windows, RegSeqRat readbacks, and the terminal Real seal;
\item provenance exactness, requiring $P$ and $N$ to source and name only the listed rows and no host inverse function, quotient function space, selected germ, global bijection theorem, ambient Real completeness principle, Lean verification, or bridge credential.
\end{enumerate}
No inverse-function NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:inverse-function-carrier}. The accepted packet displays exactly the function row, base-point and window row, derivative row, invertible approximation row, Newton--Kantorovich row, implicit-function row, Newton-iteration ledger, stream windows, regular rational readback, Real seal, transport, replay, provenance, and local name.

The analytic compatibility obligations are local to $D$ and $L$. The derivative row supplies the displayed linear data, while the linear approximation row records the inverse-witness ledger used by both the Newton and implicit-function routes.

The solving route is finite. The row $J$ lists the Newton steps, and $K$ reads that ledger as the Newton--Kantorovich contraction and root-boundary handoff. The row $I$ then repacks the same local solving data as a graph-window certificate for $F(x)=y$.

The completion-facing rows are downstream. The stream row $S$ fixes the finite windows, $Q$ supplies the regular rational readback, and $R$ provides the terminal Real seal only after the analytic and solving rows have been opened. The structural rows $H,C,P,N$ transport, replay, source, and name this same route without adding any excluded coordinate.
\end{proof}

\begin{theorem}[Inverse function local-bijection handoff]\label{thm:inverse-function-local-bijection-handoff}
Every accepted $\InverseFunctionUp$ read exported as a local bijection window factors through the displayed finite route
$$
\ImplicitFunctionUp \longmapsto \NewtonKantorovichUp \longmapsto \NewtonIterationUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
as instantiated by $I,K,J,S,Q,R$ and the analytic rows $F,B,D,L$. The consumer receives one displayed function row, one base-point and window row, one derivative row, one invertible approximation row, one Newton--Kantorovich row, one implicit-function row, one finite NewtonIteration ledger, one StreamName window row, one RegSeqRat readback row, one Real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row. The handoff is local window data only; it is not a host inverse function, not quotient function space equality, not a selected germ, not a global bijection theorem, not ambient $\RealUp$ completeness, and not bridge verification.
\end{theorem}
\begin{proof}
Project the accepted carrier $V=(F,B,D,L,K,I,J,S,Q,R,H,C,P,N)$. The local bijection read starts with the displayed function and base-window rows $F,B$, and the only linear source available to it is the pair $D,L$.

The solving route then passes through the finite Newton data. The row $J$ exposes the step ledger, $K$ reads that ledger as the Newton--Kantorovich root-boundary route, and $I$ identifies the same local solving data as an implicit-function graph window.

The L10 completion route is the final handoff. The finite windows in $S$ are read back through $Q$, and the terminal Real data appears only in $R$. Thus a Real-facing inverse-window consumer cannot bypass the finite StreamName and RegSeqRat route.

Finally $H,C,P,N$ preserve the same route under transport, replay, provenance, and local naming. Since no carrier coordinate stores a host inverse function, quotient function space, selected germ, global bijection theorem, ambient completeness theorem, or bridge credential, every exported local-bijection handoff is exhausted by the displayed finite packet.
\end{proof}

\falsifiablePrediction{Every $\InverseFunctionUp$ local-bijection read factors through one displayed function row, one base-point and window row, one derivative row, one invertible approximation row, one NewtonKantorovich row, one ImplicitFunction row, one finite NewtonIteration ledger, one StreamName finite-window row, one RegSeqRat readback row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{implicitfunction, newtonkantorovich, newtoniteration, regseqrat, streamname, real: $\InverseFunctionUp$ is not bijective to any listed sibling because it jointly carries local bijection windows, derivative and inverse-witness rows, finite Newton solving data, implicit graph-window handoff, regular rational readback, terminal Real sealing, transport, replay, provenance, and local naming as one certificate.}

\closureat{InverseFunctionUp}{seedStr}

\begin{closurestatus}{\InverseFunctionUp}
  \constructivestory{An $\InverseFunctionUp$ packet is generated from a displayed function row, a base-point and window row, a derivative row, an invertible approximation row, a NewtonKantorovich row, an ImplicitFunction row, a finite NewtonIteration ledger, StreamName windows, RegSeqRat readbacks, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:inverse-function-carrier}, \autoref{thm:inverse-function-namecert-obligations}, and \autoref{thm:inverse-function-local-bijection-handoff} seed the finite local inversion certificate over analytic rows, Newton solving rows, implicit graph-window rows, finite stream windows, regular rational readback, and Real seal data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host inverse functions, quotient function spaces, selected inverse germs, global bijection theorems, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, derivative and inverse-witness compatibility, Newton route compatibility, implicit-function handoff, L10 completion-route handoff, provenance exactness, and local naming for BEDC.Derived.InverseFunctionUp.}
\end{closurestatus}
