\chapter{A Concrete Naming Certificate for $\LocatedRealCauchyCriterionUp$}
\label{ch:concrete-instances-located-real-cauchy-criterion-namecert}
\origin{human}

Following Bishop and Bridges, the $\LocatedRealCauchyCriterionUp$ packet records the finite route by which located observations of a real sequence become a Cauchy-criterion read before a terminal real-name seal is consumed. It sits after the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Cauchy readiness surface of \autoref{ch:concrete-instances-real-cauchy-criterion-namecert}, the Real seal boundary of \autoref{ch:concrete-instances-real-namecert}, and the exact completion boundary of \autoref{ch:concrete-instances-real-completion-exact-boundary-namecert}. The packet is a located finite-observation criterion for Real and Completion consumers; it does not identify quotient streams, select a limit, invoke countable choice, decide trichotomy, compare host real values, or assert ambient Real completeness.

\begin{definition}[Located real Cauchy criterion carrier]
\label{def:located-real-cauchy-criterion-carrier}
A $\LocatedRealCauchyCriterionUp$ carrier is a finite $\BHist$ packet
$$
K=(L,S,R,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the located source-window row, exposing the finite real-sequence entries, locatedness witnesses, and precision requests inspected by the criterion.
\item $S$ is the $\StreamNameUp$ finite-window family opened from the located source windows in $L$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed StreamName windows and no other stream source.
\item $D$ is the $\DyadicRatCoreUp$ tolerance-cell row, recording requested radii, split tolerances, late-pair budgets, and dyadic comparison cells.
\item $Q$ is the $\RealCauchyCriterionUp$ output row, tying the located source windows, stream windows, regular readback, and dyadic tolerance cells to an accepted Cauchy-criterion read.
\item $E$ is the terminal $\RealUp$ seal row reached only after $L,S,R,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the located source windows, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance cells, RealCauchyCriterion output, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located precision request through $L,S,R,D,Q,E$.
\item $P$ is the $\Pkg$ provenance over $\LocatedRealCauchyCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealCauchyCriterionUp$, $\RealUp$, $\RealCompletionExactBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedRealCauchyCriterionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,S,R,D,Q,E,H,C,P,N$. It has no coordinate for quotient stream equality, a selected limit, countable choice, trichotomy, host real equality, detached completeness, or an ambient Real-completion theorem.
\end{definition}

\begin{theorem}[Located real Cauchy criterion NameCert obligations]
\label{thm:located-real-cauchy-criterion-namecert-obligations}
For an accepted $\LocatedRealCauchyCriterionUp$ carrier
$$
K=(L,S,R,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedRealCauchyCriterionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the located source-window row, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance cells, RealCauchyCriterion output, Real seal, transport, replay, provenance, and local naming row;
\item located-window exactness, requiring every observed real-sequence entry and locatedness witness to enter through $L$ before any StreamName window or regular rational readback is inspected;
\item dyadic tolerance exactness, requiring $D$ to display the requested radius, split tolerance, late-pair budget, and comparison cells used by the criterion;
\item CauchyCriterion handoff, requiring $Q$ to read only the displayed route $L,S,R,D$ before the Real seal $E$ is available;
\item seal nonescape, requiring every terminal $\RealUp$ read to pass through $E$ rather than through a quotient stream, selected limit, or host real object;
\item transport and replay stability, requiring componentwise $\hsame$ transport $H$ and displayed $\Cont$ replay $C$ to preserve the same ordered route $L,S,R,D,Q,E$;
\item provenance exhaustion, requiring $P$ and $N$ to name only this displayed route and to export no countable choice, trichotomy, host real equality, detached completeness, or ambient completion principle.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-real-cauchy-criterion-carrier}. The accepted packet displays the located source windows, StreamName windows, regular rational readback, dyadic tolerance cells, CauchyCriterion output, Real seal, and the structural rows $H,C,P,N$.

Located-window exactness is read from the order of $L,S,R$. The source observations and locatedness witnesses appear in $L$ before $S$ opens any finite stream window, and $R$ reads only through those displayed windows.

Dyadic tolerance exactness is the role of $D$. The tolerance row stores the requested radius, split budget, late-pair comparison, and dyadic cells before the CauchyCriterion output row may be consumed.

The handoff to $\RealCauchyCriterionUp$ is then finite. The row $Q$ binds the displayed $L,S,R,D$ route as the only criterion output that can reach the terminal seal $E$.

Seal nonescape follows from the carrier inventory. The terminal $\RealUp$ row is named as $E$, while quotient streams, selected limits, and host real objects are not coordinates of the packet.

Transport and replay are structural. Componentwise $\hsame$ in $H$ preserves the listed rows, and $\Cont$ replay in $C$ repeats the same route from a located precision request through $L,S,R,D,Q,E$.

Finally, provenance is exhausted by $P$ and $N$. Since the carrier has no row for countable choice, trichotomy, host real equality, detached completeness, or ambient completion, the local NameCert surface cannot export any such object.
\end{proof}

\begin{theorem}[Located real Cauchy criterion terminal seal route]
\label{thm:located-real-cauchy-criterion-terminal-seal-route}
Every terminal $\RealUp$ read of an accepted $\LocatedRealCauchyCriterionUp$ packet
$$
K=(L,S,R,D,Q,E,H,C,P,N)
$$
factors through the displayed finite route
$$
L \longmapsto S \longmapsto R \longmapsto D \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus the terminal real-name seal is reached through located source windows, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance cells, the $\RealCauchyCriterionUp$ output, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\LocatedRealCauchyCriterionUp}$ row. It exports no quotient stream, selected limit, countable choice, trichotomy, host real equality, or ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with a terminal $\RealUp$ read of an accepted packet. Projection gives the ordered rows $L,S,R,D,Q,E,H,C,P,N$, so the read starts at the located source-window surface rather than at an unbounded host stream.

The StreamName and RegSeqRat stages are downstream of $L$. The finite windows $S$ are opened from the located source row, and the regular rational readback $R$ is obtained only through those windows.

The dyadic tolerance row $D$ is downstream of that readback. It records the split tolerance and late-pair comparison cells required before the CauchyCriterion output can be accepted.

The CauchyCriterion handoff is $Q$. By \autoref{thm:located-real-cauchy-criterion-namecert-obligations}, $Q$ may read only $L,S,R,D$ before exposing the terminal Real seal $E$.

Transport, replay, provenance, and local naming do not add analytic coordinates. The rows $H,C,P,N$ preserve, replay, source, and name the same displayed route.

The excluded objects are absent from the carrier and from the NameCert obligations. Therefore no quotient stream, selected limit, countable choice, trichotomy, host real equality, or ambient Real completeness can be exported by a terminal seal read.
\end{proof}

\closureat{LocatedRealCauchyCriterionUp}{seedStr}

\begin{closurestatus}{\LocatedRealCauchyCriterionUp}
  \constructivestory{A $\LocatedRealCauchyCriterionUp$ packet is generated from located source-window rows, StreamName finite windows, RegSeqRat readback, DyadicRatCore tolerance cells, a RealCauchyCriterion output row, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-real-cauchy-criterion-carrier}, \autoref{thm:located-real-cauchy-criterion-namecert-obligations}, and \autoref{thm:located-real-cauchy-criterion-terminal-seal-route} seed the located finite-observation route from Real sequence windows to the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, located-window exactness, dyadic tolerance exactness, CauchyCriterion handoff, seal nonescape, transport stability, replay stability, and provenance exhaustion for BEDC.Derived.LocatedRealCauchyCriterionUp.}
\end{closurestatus}
