\chapter{A Concrete Naming Certificate for $\KuratowskiCompletionUp$}
\label{ch:concrete-instances-kuratowski-completion-namecert}
\origin{human}

Following Kuratowski's metric embedding theorem, Kelley-style completion, and Bishop--Bridges constructive analysis, the $\KuratowskiCompletionUp$ packet records the completion route that first embeds a source metric object into displayed distance-function rows and then seals the resulting Cauchy data as finite BEDC completion evidence. It sits after the distance-function surface of \autoref{ch:concrete-instances-kuratowski-embedding-namecert}, the completion interface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the universal handoff of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert}, and the separated uniqueness boundary of \autoref{ch:concrete-instances-separatedmetricreflection-namecert}. The chapter names the L10 metric-completion landing surface without choosing quotient representatives, asserting host function extensionality, invoking countable choice, using open-cover compactness, or assuming ambient $\RealUp$ completeness.

\begin{definition}[Kuratowski completion carrier]
\label{def:kuratowski-completion-carrier}
A $\KuratowskiCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(M,E,D,S,A,U,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric row, including the finite endpoint, distance, and Cauchy-window requests that will be completed.
\item $E$ is the accepted $\KuratowskiEmbeddingUp$ row that turns the source metric observations into displayed distance-function target rows.
\item $D$ is the distance-function readback row, exposing the $\RealUp$ distance observations used by the embedded Cauchy comparisons.
\item $S$ is the completion-seal row for the embedded Cauchy route, read through $\MetricCompletionUp$ rather than through a quotient object.
\item $A$ is the $\CauchyCompletionAdjunctionUp$ extension row that supplies the universal completion handoff for downstream consumers.
\item $U$ is the $\SeparatedMetricReflectionUp$ uniqueness row, recording that separated readback identifies only the displayed completion route.
\item $R$ is the real-distance readback row that returns finite distance observations from the sealed completion surface to the terminal $\RealUp$ distance boundary.
\item $H$ records componentwise $\hsame$ transport for the source, embedding, distance-function, completion-seal, adjunction, separated-reflection, real-readback, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from source metric reads through Kuratowski distance functions, completion sealing, adjunction extension, separated uniqueness, and real-distance readback.
\item $P$ is the $\Pkg$ provenance over $\KuratowskiCompletionUp$, $\KuratowskiEmbeddingUp$, $\MetricCompletionUp$, $\CauchyCompletionAdjunctionUp$, $\SeparatedMetricReflectionUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\KuratowskiCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, host function extensionality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Kuratowski completion NameCert obligations]
\label{thm:kuratowski-completion-namecert-obligations}
For an accepted $\KuratowskiCompletionUp$ carrier
$$
K=(M,E,D,S,A,U,R,H,C,P,N),
$$
the local $\NameCert_{\KuratowskiCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the source metric row, Kuratowski embedding row, distance-function readback row, completion-seal row, adjunction extension row, separated-reflection uniqueness row, real-distance readback row, transport, replay, provenance, and local naming row;
\item source metric exposure, requiring every endpoint, distance request, and Cauchy-window request to enter through $M$ before any completion-facing row is read;
\item distance-function embedding exposure, requiring $E$ and $D$ to display the Kuratowski distance-function route before completion sealing is available;
\item completion-seal exactness, requiring $S$ to bind the embedded Cauchy route as a $\MetricCompletionUp$ surface and not as a quotient representative;
\item adjunction extension handoff, requiring $A$ to expose every downstream extension consumer only after the same $M,E,D,S$ route has been displayed;
\item separated uniqueness readback, requiring $U$ and $R$ to return uniqueness and finite distance reads through separated-reflection and $\RealUp$ rows;
\item structural exhaustion, requiring $H,C,P,N$ to preserve, replay, source, and name only the listed route.
\end{enumerate}
No NameCert obligation is stored outside these rows, and none exports quotient completion equality, selected representatives, host function extensionality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:kuratowski-completion-carrier}. The accepted packet displays exactly the source, embedding, distance-function, completion-seal, adjunction, separated-reflection, real-readback, and structural rows.

Source metric exposure is read from $M$. Since every endpoint, distance request, and Cauchy-window request enters before the Kuratowski embedding row, the packet cannot manufacture completion data from an unrecorded metric object.

Distance-function embedding exposure is read from $E$ and $D$. The embedding row supplies the displayed Kuratowski distance-function surface, while the distance-function readback row records the corresponding $\RealUp$ observations before the completion seal is inspected.

Completion-seal exactness and adjunction extension are read from $S$ and $A$. The row $S$ seals the embedded Cauchy route as a $\MetricCompletionUp$ object, and the row $A$ exposes extension consumers only downstream of that same finite route.

Separated uniqueness and real-distance readback are then finite row checks. The row $U$ records uniqueness only through the separated-reflection boundary, and $R$ returns distance observations through the displayed real-distance surface.

Finally $H,C,P,N$ add no analytic coordinate. They transport, replay, source, and name the displayed route, so the excluded quotient, representative, host-extensionality, choice, compactness, and ambient-completeness principles have no row from which a consumer could read them.
\end{proof}

\begin{theorem}[Kuratowski completion metric-completion handoff]
\label{thm:kuratowski-completion-metric-completion-handoff}
Let
$$
K=(M,E,D,S,A,U,R,H,C,P,N)
$$
be an accepted $\KuratowskiCompletionUp$ carrier. Every L10 metric-completion consumer of $K$ receives the completion object only through the finite route
$$
M \longmapsto E,D \longmapsto S \longmapsto A \longmapsto U,R \longmapsto H,C,P,N .
$$
Thus the handoff from Kuratowski distance functions to metric completion is a displayed NameCert route over source metric rows, distance-function embedding rows, completion-seal rows, adjunction extension rows, separated-reflection uniqueness rows, real-distance readback rows, and structural $\hsame/\Cont/\Pkg/\NameCert$ rows. It is not quotient completion equality, not selected-representative data, not host function extensionality, not countable choice, not open-cover compactness, and not an ambient completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Fix an L10 metric-completion consumer of the packet. Projection gives the source metric row $M$, so the consumer starts from the displayed endpoint, distance, and Cauchy-window requests.

Apply the Kuratowski embedding row $E$ and distance-function readback row $D$. These rows move the source metric observations into displayed distance-function data before any completion-facing object is available.

The completion-seal row $S$ is therefore attached to the embedded route. Since $S$ is a row of the finite carrier, it gives a $\MetricCompletionUp$ seal and not a quotient class with a selected representative.

The adjunction extension row $A$ supplies the universal completion handoff. Any downstream extension consumer must read through the same $M,E,D,S$ chain before seeing $A$.

Separated uniqueness and real-distance readback are downstream of that handoff. The rows $U$ and $R$ expose only separated-reflection uniqueness and displayed $\RealUp$ distance observations.

Transport, replay, provenance, and local naming close the route. The rows $H,C,P,N$ preserve the listed data componentwise, so no host function extensionality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness can be exported by the packet.
\end{proof}

\closureat{KuratowskiCompletionUp}{seedStr}

\begin{closurestatus}{\KuratowskiCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kuratowski-completion-carrier}, \autoref{thm:kuratowski-completion-namecert-obligations}, and \autoref{thm:kuratowski-completion-metric-completion-handoff} seed the finite Kuratowski distance-function route into metric-completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host function extensionality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, distance-function embedding exposure, completion-seal exactness, adjunction extension handoff, separated uniqueness readback, real-distance readback, and structural replay for BEDC.Derived.KuratowskiCompletionUp.}
  \constructivestory{A $\KuratowskiCompletionUp$ packet is generated from source metric rows, Kuratowski distance-function embedding rows, completion-seal rows, adjunction extension rows, separated-reflection uniqueness rows, Real distance-readback rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
