\chapter{A Concrete Naming Certificate for $\LocatedMetricCompletionUp$}
\label{ch:concrete-instances-located-metric-completion-namecert}
\origin{human}

Following Bishop and Bridges and Kelley, the $\LocatedMetricCompletionUp$ packet records the L10 metric-completion boundary where located source data are carried into finite completion evidence without quotienting Cauchy names. It sits between the located metric source of \autoref{ch:concrete-instances-locatedmetric-namecert}, the completion packet of \autoref{ch:concrete-instances-metriccompletion-namecert}, the embedding surface of \autoref{ch:concrete-instances-completionembedding-namecert}, the separated uniqueness row of \autoref{ch:concrete-instances-separatedmetric-namecert}, and the finite readback interfaces of \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}. The packet is a NameCert seed for displayed completion-facing reads over a located metric source; it is not a quotient completion, a representative selector, a countable-choice device, an open-cover compactness principle, host equality, an ambient complete metric space, or a completeness theorem for $\RealUp$.

\begin{definition}[LocatedMetricCompletion carrier]
\label{def:located-metric-completion-carrier}
A $\LocatedMetricCompletionUp$ carrier is a finite $\BHist$ packet
$$
L=(X,M,F,D,E,R,S,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source $\LocatedMetricUp$ row, including the displayed metric distance, locatedness witness, and finite observation histories used by completion consumers.
\item $M$ is the $\MetricCompletionUp$ row that exposes the completion-facing interface over the same source data.
\item $F$ is either a $\CauchyFilterUp$ cofinal-evidence row or an empty marker when the displayed completion route uses directed nets.
\item $D$ is either a $\CauchyNetUp$ directed-window row or an empty marker when the displayed completion route uses Cauchy filters.
\item $E$ is the $\CompletionEmbeddingUp$ row by which located source observations enter the completion-facing surface.
\item $R$ is the finite $\RegSeqRatUp$ or $\RealUp$ readback row used for numerical tolerance requests.
\item $S$ is the $\SeparatedMetricUp$ row that identifies displayed limit readings only through the zero-distance route available from the located source and completion packet.
\item $H$ records componentwise $\hsame$ transport for the located source, metric-completion row, Cauchy evidence branch, embedding row, readback row, separatedness row, replay row, provenance row, and local naming row.
\item $C$ records the displayed $\Cont$ replay from located metric observations to the metric-completion interface, Cauchy-filter or Cauchy-net evidence, completion embedding, finite readback, separated comparison, provenance, and local name.
\item $P$ is the $\Pkg$ provenance over $\LocatedMetricCompletionUp$, $\LocatedMetricUp$, $\MetricCompletionUp$, $\CauchyFilterUp$, $\CauchyNetUp$, $\CompletionEmbeddingUp$, $\RegSeqRatUp$, $\RealUp$, $\SeparatedMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedMetricCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, countable choice, open-cover compactness, host equality, ambient complete metric spaces, or detached completeness of $\RealUp$.
\end{definition}

\begin{theorem}[LocatedMetricCompletion NameCert obligations]
\label{thm:located-metric-completion-namecert-obligations}
For an accepted $\LocatedMetricCompletionUp$ carrier $L=(X,M,F,D,E,R,S,H,C,P,N)$, the local $\NameCert_{\LocatedMetricCompletionUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed located metric source, metric-completion row, selected Cauchy evidence branch, completion embedding, finite readback, separatedness row, transports, replay route, provenance, and local name;
\item located-source handoff, requiring every completion-facing read to begin with $X$ before the metric-completion row $M$ or any Cauchy evidence row is consumed;
\item cofinal evidence selection, requiring each accepted read to use exactly one visible branch, either the $\CauchyFilterUp$ row $F$ or the $\CauchyNetUp$ row $D$;
\item embedding coverage, requiring source observations to reach the completion surface only through the $\CompletionEmbeddingUp$ row $E$;
\item finite readback compatibility, requiring numerical tolerance requests to pass through $R$ before separated comparison or local naming;
\item separated uniqueness, requiring equality of displayed completion reads to pass through the $\SeparatedMetricUp$ row $S$ after the located source, completion interface, Cauchy evidence branch, embedding, and readback have been replayed;
\item ledger non-escape, stating that no quotient completion equality, selected representative, countable choice, open-cover compactness, host equality, ambient complete metric space, or $\RealUp$ completeness theorem is exported.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-metric-completion-carrier}. The tuple displays the located source, metric-completion row, filter or net branch, embedding row, finite readback, separatedness row, and structural support rows.

The located-source handoff is forced by the order of the replay row $C$. It reads $X$ first, then $M$, and only then the selected cofinal evidence branch $F$ or $D$.

Cofinal evidence selection is local to the carrier. A filter-presented read consumes $F$ while $D$ is empty, and a net-presented read consumes $D$ while $F$ is empty, so the packet exposes one completion route before $E$ and $R$ are inspected.

Embedding coverage follows from the presence of $E$ as the only source-to-completion coordinate. The readback row $R$ handles tolerance requests, and the separatedness row $S$ handles equality of displayed limit readings after the earlier rows have been replayed.

The rows $H,C,P,N$ transport, replay, package, and name exactly that finite route. Since no remaining coordinate names quotient equality, selected representatives, choice, compactness, host equality, ambient completeness, or $\RealUp$ completeness, none of those principles can be read from the local certificate.
\end{proof}

\begin{theorem}[LocatedMetricCompletion source handoff]
\label{thm:located-metric-completion-source-handoff}
Let $L=(X,M,F,D,E,R,S,H,C,P,N)$ be an accepted $\LocatedMetricCompletionUp$ packet. Every completion-facing read of $L$ factors through the finite route
$$
X\longmapsto M\longmapsto (F\ \hbox{or}\ D)\longmapsto E\longmapsto R\longmapsto S\longmapsto H,C,P,N ,
$$
where $X$ is the $\LocatedMetricUp$ source row, $M$ is the $\MetricCompletionUp$ row, $F$ or $D$ is the displayed $\CauchyFilterUp$ or $\CauchyNetUp$ evidence, $E$ is the $\CompletionEmbeddingUp$ row, and $R$ is the $\RegSeqRatUp$ or $\RealUp$ readback row.
\end{theorem}
\begin{proof}
Begin with the source row $X$. A completion-facing consumer first reads the located metric observations, including the displayed distance and locatedness evidence.

The completion interface is then read through $M$. The cofinal evidence branch is selected next: either the Cauchy-filter row $F$ or the Cauchy-net row $D$ supplies the visible late-window evidence.

The source observation enters completion-facing form only through $E$. Numerical requests then pass through the finite readback row $R$, and equality or uniqueness requests pass through the separatedness row $S$.

Finally, $H,C,P,N$ transport and name the same route. No other coordinate is available, so every completion-facing read has the displayed factorization.
\end{proof}

\begin{theorem}[LocatedMetricCompletion ledger non-escape]
\label{thm:located-metric-completion-nonescape}
For an accepted $\LocatedMetricCompletionUp$ carrier $L=(X,M,F,D,E,R,S,H,C,P,N)$, every exported completion read, tolerance read, embedding read, and separated comparison is exhausted by the rows
$$
X,M,F,D,E,R,S,H,C,P,N .
$$
Consequently the packet excludes quotient completion equality, selected representatives, countable choice, open-cover compactness, host equality, ambient complete metric spaces, and detached completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Completion reads begin at the located source $X$ and the metric-completion row $M$. They then pass through exactly one displayed Cauchy evidence branch, either $F$ or $D$.

Embedding reads are confined to $E$, and numerical tolerance reads are confined to $R$. The separatedness row $S$ handles comparison of displayed limit readings only after those earlier coordinates have been replayed.

The support rows $H,C,P,N$ preserve and name that same finite ledger. Because the carrier lists no coordinate for quotient equality, representative selection, countable choice, open-cover compactness, host equality, ambient completeness, or $\RealUp$ completeness, those principles cannot be exported by the packet.
\end{proof}

\closureat{LocatedMetricCompletionUp}{seedStr}

\begin{closurestatus}{\LocatedMetricCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-metric-completion-carrier}, \autoref{thm:located-metric-completion-namecert-obligations}, \autoref{thm:located-metric-completion-source-handoff}, and \autoref{thm:located-metric-completion-nonescape} seed the finite located metric completion packet over located source data, metric-completion evidence, Cauchy-filter or Cauchy-net branches, completion embedding, finite readback, and separated uniqueness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, countable choice, open-cover compactness, host equality, ambient complete metric spaces, $\RealUp$ completeness, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, located-source handoff, cofinal evidence selection, embedding coverage, finite readback, separated uniqueness, and ledger non-escape for BEDC.Derived.LocatedMetricCompletionUp.}
  \constructivestory{A $\LocatedMetricCompletionUp$ packet is generated from a located metric source, metric-completion row, displayed Cauchy-filter or Cauchy-net evidence, completion embedding, finite readback, separatedness row, componentwise $\hsame$ transports, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}
\end{closurestatus}
