\chapter{A Concrete Naming Certificate for $\CompletionPreservesSeparableUp$}
\label{ch:concrete-instances-completion-preserves-separable-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and the Bourbaki--Kelley separability tradition, the $\CompletionPreservesSeparableUp$ packet records the finite BEDC preservation bridge from a separable source metric to separable completion data. It reads the source surfaces of \autoref{ch:concrete-instances-separablemetric-namecert} and \autoref{ch:concrete-instances-countable-dense-subset-namecert}, the existing route of \autoref{ch:concrete-instances-separable-completion-namecert}, and the completion interface of \autoref{ch:concrete-instances-metriccompletion-namecert}. Its finite observation spine is the L10 route through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$, so the bridge preserves displayed density through windows and tolerance ledgers rather than through quotient equality, countable choice, selected representatives, or host equality of completed points.

\begin{definition}[CompletionPreservesSeparable carrier]\label{def:completion-preserves-separable-carrier}
A $\CompletionPreservesSeparableUp$ carrier is a finite $\BHist$ packet
$$
Q=(M,D,C,W,T,R,I,H,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source $\MetricUp$ and $\SeparableMetricUp$ row. It records the metric carrier, distance classifier, and countable-name separability surface over the source histories.
\item $D$ is the $\CountableDenseSubsetUp$ row. It stores the indexed dense schedule and the finite request windows through which source density is observed.
\item $C$ is the $\SeparableCompletionUp$ and $\MetricCompletionUp$ row. It records the completion-facing admission route reached from the same source metric and the same dense schedule.
\item $W$ is the $\StreamNameUp$ finite-window row used to inspect dense indices, source Cauchy observations, and completion-facing name segments.
\item $T$ is the $\DyadicRatCoreUp$ and $\RealUp$ tolerance ledger attached to $W$. It carries dyadic scales, Real distance boundaries, and comparison budgets for the dense-image request.
\item $R$ is the $\RegSeqRatUp$ readback row produced from $D,W,T$ before the completion seal is consulted.
\item $I$ is the dense-image handoff row. It records that a completion request is answered by first exposing an indexed source dense point through $D,W,T,R$ and then passing through the completion seal $C$.
\item $H$ records componentwise $\hsame$ transport for the source metric, dense schedule, completion row, stream windows, tolerance ledger, readback, image handoff, provenance, and local naming rows.
\item $P$ is the $\Pkg$ provenance over $\CompletionPreservesSeparableUp$, $\MetricUp$, $\SeparableMetricUp$, $\CountableDenseSubsetUp$, $\SeparableCompletionUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompletionPreservesSeparableUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite preservation packet. It has no coordinate for quotient completion equality, selected dense representatives, countable choice, host equality of completion points, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CompletionPreservesSeparable NameCert obligations]\label{thm:completion-preserves-separable-namecert-obligations}
For every accepted $\CompletionPreservesSeparableUp$ carrier $Q=(M,D,C,W,T,R,I,H,P,N)$, the local $\NameCert_{\CompletionPreservesSeparableUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier exposure for the displayed source metric and separable row, countable dense schedule, separable-completion and metric-completion row, stream windows, tolerance ledger, regular readback, dense-image handoff, transport, provenance, and local naming rows;
\item source-density admission, requiring each completion-density request to start from the displayed countable dense schedule $D$ over the source metric row $M$;
\item finite-window inspection, requiring dense indices and completion-facing name segments to pass through the same $\StreamNameUp$ row $W$;
\item tolerance and readback discipline, requiring $\DyadicRatCoreUp$ or $\RealUp$ comparison data in $T$ and $\RegSeqRatUp$ readback in $R$ before the completion row is exposed;
\item completion-image handoff, requiring the row $I$ to bind the selected source dense observation to the completion route $C$ without storing a host-level completed point;
\item classifier transport, requiring comparisons of accepted packets to transport $M,D,C,W,T,R,I$ together through $H$;
\item nonescape, excluding quotient completion equality, selected dense representatives, countable-choice selectors, host equality of completion points, open-cover compactness, and ambient Real completeness from the packet.
\end{enumerate}
No completion-preservation obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:completion-preserves-separable-carrier}. The projection exposes exactly the source metric row $M$, countable dense schedule $D$, completion row $C$, finite windows $W$, tolerance ledger $T$, regular readback $R$, dense-image handoff $I$, and structural rows $H,P,N$.

Source-density admission is read before the completion row. A density request first displays an index in $D$ over the same source metric row $M$, then opens the finite $\StreamNameUp$ window $W$ attached to that request.

The tolerance and readback rows mediate the request. The packet reads the dyadic or Real comparison data $T$ and the regular rational handoff $R$ before it exposes the completion-facing row $C$.

The dense-image handoff is the row $I$. It binds the displayed source dense observation to the completion route without adding a selected completed representative, quotient equality, or host-level equality of completion points.

Finally, $H,P,N$ transport, source, and name the same finite route. Since no carrier coordinate stores the excluded quotient, choice, host-equality, compactness, or ambient-completeness data, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[CompletionPreservesSeparable dense-image handoff]\label{thm:completion-preserves-separable-dense-image-handoff}
Every complete-separable or completion-facing consumer of an accepted $\CompletionPreservesSeparableUp$ carrier $Q=(M,D,C,W,T,R,I,H,P,N)$ reads the finite route
$$
M,D \longmapsto W \longmapsto T \longmapsto R \longmapsto I \longmapsto C \longmapsto H,P,N
$$
before it reads the public packet. Thus separability of the completion is exported through displayed source dense data, finite windows, tolerance checks, regular readback, and the dense-image handoff. The route exports no quotient completion equality, no selected dense representative, no countable-choice selector, no host equality of completed points, and no ambient Real-completeness datum.
\end{theorem}
\begin{proof}
Begin with a complete-separable or completion-facing read of $Q$. Carrier admission gives the consumer the source metric and source dense schedule only as the displayed pair $M,D$.

Replay the finite observation route. The request opens the $\StreamNameUp$ window $W$, reads the dyadic or Real tolerance ledger $T$, and obtains the $\RegSeqRatUp$ readback $R$ before any completion-facing image is available.

The image row $I$ is downstream of those source observations. It records the handoff from the displayed source dense point to the completion route $C$, so the consumer sees density in the completion only through the same finite source data.

Transport, provenance, and local naming through $H,P,N$ preserve that route rather than adding a second completion object. Therefore every downstream consumer factors through source density, finite observation, tolerance, readback, image handoff, and completion admission before it reads the public packet.

The excluded quotient, selected-representative, choice, host-equality, and ambient-completeness data have no coordinate in the carrier.
\end{proof}

\closureat{CompletionPreservesSeparableUp}{seedStr}
\begin{closurestatus}{\CompletionPreservesSeparableUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:completion-preserves-separable-carrier}, \autoref{thm:completion-preserves-separable-namecert-obligations}, and \autoref{thm:completion-preserves-separable-dense-image-handoff} seed the finite preservation bridge from source separability to separable completion data through dense schedules, stream windows, dyadic or Real tolerances, regular readbacks, and dense-image handoff rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected dense representatives, countable choice, host equality of completion points, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, source-density admission, finite-window inspection, tolerance and readback discipline, completion-image handoff, classifier transport, nonescape, and dense-image handoff for BEDC.Derived.CompletionPreservesSeparableUp.}
  \constructivestory{A $\CompletionPreservesSeparableUp$ packet is generated from a MetricUp and SeparableMetricUp source row, a CountableDenseSubsetUp schedule, a SeparableCompletionUp and MetricCompletionUp row, finite StreamName windows, DyadicRatCore or RealUp tolerance data, a RegSeqRat readback, a dense-image handoff row, componentwise hsame transport, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
