\chapter{A Concrete Naming Certificate for $\CompactMetricSubspaceUp$}
\label{ch:concrete-instances-compact-metric-subspace-namecert}
\origin{human}

Following Bishop--Bridges compact metric practice and the Kelley subspace reading of finite metric data, the $\CompactMetricSubspaceUp$ packet records a compact subspace of a compact metric packet by finite NameCert rows. It sits over the subspace metric interface of \autoref{ch:concrete-instances-metric-subspace-namecert}, the finite-net compact metric surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the total-boundedness rows of \autoref{ch:concrete-instances-totallybounded-namecert}, the complete metric limit rows of \autoref{ch:concrete-instances-completemetric-namecert}, and the stream and real readback interfaces of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet is a standard compact-subspace certificate for later compact-continuity and completion arguments; it is not an open-cover compactness theorem, a nearest-point selector, a quotient subset equality principle, a trichotomy principle, or an ambient $\RealUp$ completeness claim.

\begin{definition}[CompactMetricSubspace carrier]
\label{def:compact-metric-subspace-carrier}
A $\CompactMetricSubspaceUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,K,T,L,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\MetricSubspaceUp$ admission packet. It records the parent metric row, the displayed admission row, the inherited distance ledger, the restricted replay path, and the local subspace name.
\item $K$ is the ambient $\CompactMetricUp$ finite-net packet. It supplies only finite net data, mesh budgets, coverage witnesses, and compact-metric admission rows for the parent metric source.
\item $T$ records $\TotallyBoundedUp$ witnesses restricted to admitted points. Each net point exposed to the subspace consumer is checked through the admission row of $S$ before it is used as a covering center.
\item $L$ records $\CompleteMetricUp$ limit closure for regular Cauchy streams whose displayed observations remain admitted by $S$ and whose parent limit row is admitted by the same subspace predicate.
\item $W$ records $\StreamNameUp$ windows for the subspace Cauchy streams consumed by $L$, including the finite late-distance windows used by total boundedness and completeness consumers.
\item $R$ records $\RegSeqRatUp$ readbacks of the rational mesh, modulus, and late-distance budgets used by $K,T,L,W$.
\item $E$ records $\RealUp$ seals for the displayed distance comparisons and limit-read confirmations that are already routed through $S,K,T,L,W,R$.
\item $H$ records componentwise $\hsame$ transport for the subspace admission packet, compact metric packet, total-boundedness witnesses, completeness closure row, stream windows, regular rational readbacks, real seals, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
S,K,T,L,W,R,E \longmapsto H,C,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactMetricSubspaceUp$, $\MetricSubspaceUp$, $\CompactMetricUp$, $\TotallyBoundedUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CompactMetricSubspaceUp}$ row.
\end{enumerate}
The classifier compares packets only through $S,K,T,L,W,R,E,H,C,P,N$. It has no coordinate for open-cover compactness, choice-selected nearest points, quotient subset equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CompactMetricSubspace NameCert obligations]
\label{thm:compact-metric-subspace-namecert-obligations}
For every accepted $\CompactMetricSubspaceUp$ carrier
$$
Q=(S,K,T,L,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\CompactMetricSubspaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the metric subspace packet, ambient compact metric packet, restricted total-boundedness witnesses, complete metric limit-closure row, stream windows, regular rational readbacks, real seals, transport, replay, provenance, and local naming rows;
\item subspace admission stability, requiring every compact-net center, stream observation, candidate limit, rational mesh read, and real seal to pass through the $\MetricSubspaceUp$ admission row before it is exported;
\item finite-net restriction, requiring every $\CompactMetricUp$ net read used by the subspace packet to be accompanied by admitted centers and the inherited distance route of the metric subspace packet;
\item total-bounded and complete-metric compatibility, requiring the $\TotallyBoundedUp$ witnesses and $\CompleteMetricUp$ limit-closure row to name the same restricted distance ledger and the same admitted stream windows;
\item classifier transport, requiring $\hsame$ transport in $H$ to preserve the admission row, finite-net rows, total-boundedness witnesses, completion closure, stream windows, rational readbacks, real seals, replay, provenance, and local name;
\item ledger exhaustion, requiring $C,P,N$ to replay, source, and name only the displayed finite route and to export no open-cover compactness, choice-selected nearest point, quotient subset equality, trichotomy principle, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
No CompactMetricSubspace obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Carrier admission is projection from \autoref{def:compact-metric-subspace-carrier}. The tuple displays exactly the subspace packet, ambient compact metric packet, total-boundedness witnesses, completion closure row, stream windows, rational readbacks, real seals, transport, replay, provenance, and local naming rows.

Subspace admission stability is forced by the position of $S$. A compact-net center, stream observation, candidate limit, rational budget, or real seal is visible to the subspace consumer only after the parent point classifier and the admission row recorded by $S$ have both been replayed.

Finite-net restriction uses $K$ together with $T$. The ambient $\CompactMetricUp$ row supplies finite nets, while the restricted total-boundedness row exposes only those centers that survive the admission check and the inherited distance route of \autoref{ch:concrete-instances-metric-subspace-namecert}.

Compatibility of total boundedness and completeness uses $L$ and $W$. The same admitted stream windows feed the late-distance reads for total boundedness and the limit-closure reads for completeness, so the packet cannot switch to a second distance ledger or a second stream name.

Transport and exhaustion are recorded by $H,C,P,N$. Since the carrier has no coordinate outside $S,K,T,L,W,R,E,H,C,P,N$, the excluded open-cover, nearest-point, quotient, trichotomy, and ambient real-completeness principles cannot be exported by the local name.
\end{proof}

\begin{theorem}[Inherited total-boundedness and completeness]
\label{thm:compact-metric-subspace-inherited-total-bounded-completeness}
Let $Q=(S,K,T,L,W,R,E,H,C,P,N)$ be an accepted $\CompactMetricSubspaceUp$ carrier. Every subspace compactness read exported by $Q$ factors through the finite route
$$
\MetricSubspaceUp,\CompactMetricUp,\TotallyBoundedUp,\CompleteMetricUp
\longrightarrow \StreamNameUp,\RegSeqRatUp,\RealUp
\longrightarrow H,C,P,N .
$$
Consequently a downstream completion or compact-continuity consumer receives total-boundedness witnesses only with admitted centers, completeness witnesses only for admitted regular streams whose limit row is admitted, and distance comparisons only through the inherited $\MetricSubspaceUp$ distance ledger. The exported packet contains no open-cover compactness, choice-selected nearest-point data, quotient subset equality, trichotomy, or ambient $\RealUp$ completeness assertion.
\end{theorem}

\begin{proof}
Project the accepted carrier and begin with a total-boundedness read. The $\CompactMetricUp$ row $K$ supplies a finite net at the requested rational budget, and the restricted witness row $T$ filters the displayed centers through the admission row of $S$ before the inherited distance ledger may be read.

For a completeness read, use the $\StreamNameUp$ windows in $W$ and the rational readbacks in $R$ to expose the regular Cauchy budgets consumed by $L$. The limit row is the parent $\CompleteMetricUp$ limit row only after the admission predicate of $S$ accepts it.

The real seals in $E$ confirm the displayed distance and limit comparisons already routed through $S,K,T,L,W,R$. They do not create a new completeness principle for $\RealUp$; they name the finite comparisons used by the packet.

Finally transport by $H$ and replay by $C$ keep the same rows under classifier comparison, while $P,N$ source and name the route. Thus completion and compact-continuity consumers see exactly the inherited total-bounded and complete-metric data, with the listed nonconstructive and quotient principles absent from the carrier.
\end{proof}

\begin{theorem}[Real-seal nonescape]
\label{thm:compact-metric-subspace-real-seal-nonescape}
For an accepted $\CompactMetricSubspaceUp$ carrier $Q=(S,K,T,L,W,R,E,H,C,P,N)$, every $\RealUp$ seal exported by $E$ is downstream of an admitted $\MetricSubspaceUp$ distance read, a $\RegSeqRatUp$ rational budget read, and the relevant $\StreamNameUp$ or finite-net window. Hence a consumer cannot use $Q$ to infer ambient $\RealUp$ completeness, trichotomy, quotient subset equality, a selected nearest point, or open-cover compactness.
\end{theorem}

\begin{proof}
Read a real seal from $E$. By carrier admission, the seal is not a standalone real-analysis row; it is indexed by the displayed distance or limit comparison already named by $S,K,T,L,W,R$.

If the seal concerns a finite-net distance comparison, the route first checks the subspace admission row in $S$, then reads the compact metric net in $K$, the restricted total-bounded witness in $T$, and the rational budget in $R$.

If the seal concerns a limit comparison, the route first checks the same subspace admission row, then reads the stream window in $W$, the completeness closure row in $L$, and the rational readback in $R$.

The transport, replay, provenance, and naming rows $H,C,P,N$ preserve only these finite dependencies. Since no separate $\RealUp$ completeness coordinate, trichotomy coordinate, quotient row, nearest-point selector, or open-cover compactness row appears in the carrier, none can escape through the real-seal surface.
\end{proof}

\closureat{CompactMetricSubspaceUp}{seedStr}

\begin{closurestatus}{\CompactMetricSubspaceUp}
  \constructivestory{A $\CompactMetricSubspaceUp$ packet is generated from a MetricSubspaceUp admission packet, CompactMetricUp finite-net data, restricted TotallyBoundedUp witnesses, CompleteMetricUp limit closure, StreamNameUp windows, RegSeqRatUp readbacks, RealUp seals, hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-metric-subspace-carrier}, \autoref{thm:compact-metric-subspace-namecert-obligations}, \autoref{thm:compact-metric-subspace-inherited-total-bounded-completeness}, and \autoref{thm:compact-metric-subspace-real-seal-nonescape} seed the finite compact-subspace interface over metric subspace admission, compact finite nets, total boundedness, completeness, stream windows, rational readbacks, and real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, choice-selected nearest points, quotient subset equality, trichotomy, ambient RealUp completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, subspace admission stability, finite-net restriction, total-bounded and complete-metric compatibility, classifier transport, and ledger exhaustion for BEDC.Derived.CompactMetricSubspaceUp.}
\end{closurestatus}
