\chapter{A Concrete Naming Certificate for $\KonigLemmaUp$}
\label{ch:concrete-instances-konig-lemma-namecert}
\origin{human}

Following Koenig's lemma for finitely branching trees, Brouwer's spread reading of prefix trees, and Bishop--Bridges finite evidence, $\KonigLemmaUp$ records the L10 finite-prefix boundary where tree and branch arguments may be inspected without choosing an infinite branch. The packet sits after the Boolean prefix surface of \autoref{ch:concrete-instances-cantorspace-namecert}, the finite fan boundary of \autoref{ch:concrete-instances-fantheorem-namecert}, and the barred-spread replay of \autoref{ch:concrete-instances-brouwer-bar-induction-namecert}. It exposes finite frontiers, candidate prefixes, Cantor-space prefix reads, fan/bar handoffs, transport, replay, provenance, and local naming; it does not export weak Koenig principles as global rules, open-cover compactness, quotient streams, selected infinite paths, or $\RealUp$ completeness.

\begin{definition}[KoenigLemma carrier]
\label{def:konig-lemma-carrier}
A $\KonigLemmaUp$ carrier is a finite $\BHist$ packet
$$
K=(T,F,W,Q,S,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the finitely branching prefix-tree row. It records the displayed root, finite successor lists, prefix closure checks, and extension rows, with each local branching list read through $\ListUp$ and each edge decision read through $\BoolUp$.
\item $F$ is the finite frontier ledger. It lists the currently inspected frontier prefixes, the finite window cut through $T$, and the local evidence that each retained node either extends inside the window or is recorded as a boundary node for the current request.
\item $W$ is the branch-candidate prefix row. It stores a finite compatible chain of prefixes read from $T$ and $F$, not a completed path and not a choice-selected branch.
\item $Q$ is the $\CantorSpaceUp$ prefix-reading row. It reads every Boolean branch decision through finite $\StreamNameUp$ windows, $\BoolUp$ observations, and $\ListUp$ prefix spines.
\item $S$ is the $\FanTheoremUp$ and $\BrouwerBarInductionUp$ boundary row. It records the finite fan/bar route used when a consumer asks whether the displayed frontier blocks the inspected candidate prefix.
\item $A$ is the local classifier row. It compares accepted packets by the displayed tree, frontier, window, candidate-prefix, Cantor-prefix, and fan/bar rows, with no coordinate for quotient path equality or host function extensionality.
\item $H$ records componentwise $\hsame$ transport for the tree, frontier, window, candidate-prefix, Cantor-prefix, fan/bar, classifier, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite tree request through prefix restriction, successor inspection, frontier lookup, candidate-prefix readback, Cantor-space prefix reading, fan/bar boundary use, classifier transport, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\KonigLemmaUp$, $\CantorSpaceUp$, $\FanTheoremUp$, $\BrouwerBarInductionUp$, $\StreamNameUp$, $\BoolUp$, $\ListUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\KonigLemmaUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these finite rows. It has no coordinate for a selected infinite branch, quotient path space, host function equality, open-cover compactness, weak Koenig principles as ambient rules, or $\RealUp$ completeness.
\end{definition}

\begin{theorem}[KoenigLemma NameCert obligations]
\label{thm:konig-lemma-namecert-obligations}
For every accepted $\KonigLemmaUp$ carrier
$$
K=(T,F,W,Q,S,A,H,C,P,N),
$$
the local $\NameCert_{\KonigLemmaUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the finitely branching prefix-tree row, finite frontier ledger, branch-candidate prefix row, Cantor-space prefix-reading row, fan/bar boundary row, classifier row, transport row, replay row, provenance row, and local naming row;
\item classifier transport through the componentwise rows listed in \autoref{def:konig-lemma-carrier};
\item prefix-extension stability, requiring every shorter candidate prefix and every displayed one-step extension to reuse the matching rows already present in $T,F,W,Q$;
\item branch-frontier replay, requiring every consumer route that asks for a branch obstruction or branch continuation to pass through the finite frontier ledger and the $S$ fan/bar boundary row;
\item non-escape, excluding selected infinite branches, weak Koenig principles as global rules, quotient path spaces, host function equality, open-cover compactness, and $\RealUp$ completeness.
\end{enumerate}
No local obligation is stored outside the displayed packet.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:konig-lemma-carrier}. The accepted packet exposes only the tree, frontier, candidate-prefix, Cantor-prefix, fan/bar, classifier, transport, replay, provenance, and naming rows.

Classifier transport is componentwise. Two accepted packets compare through the displayed prefix-tree and frontier rows first, then through the candidate-prefix row, Cantor-space prefix reads, and fan/bar boundary row. The structural rows $H,C,P,N$ transport and name that same finite comparison.

Prefix-extension stability is inherited from the retained prefix tree. A shorter prefix is a subrow already visible in $T$ and $W$, while a displayed one-step extension is one of the finite successor rows listed in $T$ and checked against $F$.

Branch-frontier replay is finite. A consumer asking whether the current window blocks or extends a candidate prefix must read the frontier ledger $F$ and then the fan/bar boundary row $S$; the route supplies only displayed prefix and boundary evidence.

Coordinate exhaustion gives non-escape. Since the carrier has no slot for a completed path, quotient path equality, host function extensionality, open-cover compactness, weak Koenig rules as ambient principles, or $\RealUp$ completeness, none of those objects can be exported by the local certificate.
\end{proof}

\begin{theorem}[KoenigLemma Cantor--fan boundary]
\label{thm:konig-lemma-cantor-fan-boundary}
Every consumer route from an accepted $\KonigLemmaUp$ carrier factors through
$$
\CantorSpaceUp,\ \FanTheoremUp,\ \BrouwerBarInductionUp,\ \StreamNameUp,\ \BoolUp,\ \ListUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
The route may inspect finite tree prefixes, frontier windows, candidate-prefix rows, Cantor-space Boolean prefix reads, and fan/bar boundary rows. It exports no choice-selected infinite branch, quotient path space, host function equality, open-cover compactness, weak Koenig principle as a global rule, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project a consumer route from the accepted carrier of \autoref{def:konig-lemma-carrier}. The first visible tree data are finite prefix rows in $T$ and finite frontier rows in $F$.

The candidate-prefix read is then $W$. Its Boolean decisions are not host functions; they are read through the $\CantorSpaceUp$ row $Q$, which itself routes through $\StreamNameUp$ windows, $\BoolUp$ observations, $\ListUp$ spines, and the surrounding $\BHist$ packet.

When the consumer asks whether the current frontier blocks or extends the candidate prefix, the route enters $S$. That row is exactly the finite $\FanTheoremUp$ and $\BrouwerBarInductionUp$ boundary over the displayed prefix window.

Finally $H,C,P,N$ close the route by $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming. No coordinate remains for a selected infinite branch, quotient path space, host function equality, open-cover compactness, a global weak Koenig rule, or $\RealUp$ completeness, so the stated factorization is exhaustive.
\end{proof}

\closureat{KonigLemmaUp}{seedStr}

\begin{closurestatus}{\KonigLemmaUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:konig-lemma-carrier}, \autoref{thm:konig-lemma-namecert-obligations}, and \autoref{thm:konig-lemma-cantor-fan-boundary} seed the finite-prefix tree boundary over Cantor-space prefix reads and fan/bar rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close choice-selected branches, weak Koenig principles as global rules, open-cover compactness, quotient streams, quotient path spaces, host function equality, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, prefix-extension stability, branch-frontier replay, Cantor-space prefix reading, fan/bar boundary routing, and non-escape for BEDC.Derived.KonigLemmaUp.}
  \constructivestory{A $\KonigLemmaUp$ packet is generated from a finitely branching prefix-tree row, a finite frontier ledger, a branch-candidate prefix row, a CantorSpace prefix-reading row, a FanTheorem and BrouwerBarInduction boundary row, classifier transport, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
