\chapter{A Concrete Naming Certificate for $\SignedDistanceUp$}
\label{ch:concrete-instances-signed-distance-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\SignedDistanceUp$ packet records the finite route by which a located metric source exposes a signed distance surface without importing a host real-valued distance function. The packet is admitted only as metric, locatedness, apartness, dyadic-budget, regular-readback, and real-seal rows: its metric side is anchored in \autoref{ch:concrete-instances-metric-namecert}, its located-source side in \autoref{ch:concrete-instances-locatedspace-namecert}, its signed separation side in \autoref{ch:concrete-instances-apartnessreal-namecert}, and its L10 readback spine in \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[SignedDistance carrier]
\label{def:signed-distance-carrier}
A $\SignedDistanceUp$ carrier is a finite $\BHist$ packet
$$
S=(M,L,A,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ distance row, recording the finite source and target observations, the metric comparison surface, and the triangle-compatible route through which distance requests are read.
\item $L$ is the $\LocatedSpaceUp$ source row, recording the displayed located subset or located family whose boundary is being queried.
\item $A$ is the $\ApartnessRealUp$ signed-side or separation row, recording which finite side of the located boundary supplies the positive separation evidence.
\item $D$ is the $\DyadicRatCoreUp$ budget row, carrying the rational tolerance, sign threshold, and comparison budget used by the signed-distance request.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the metric observations, dyadic budget, and signed-side comparisons.
\item $E$ is the $\RealUp$ seal reached by the displayed regular readback after $M,L,A,D,R$ have been exposed.
\item $H$ records componentwise $\hsame$ transport for the metric row, located-source row, signed-side row, dyadic budget, regular readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of every signed-distance consumer route through
$$
M,L,A,D,R \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\SignedDistanceUp$, $\MetricSpaceUp$, $\LocatedSpaceUp$, $\ApartnessRealUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SignedDistanceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,L,A,D,R,E,H,C,P,N$. It has no coordinate for a host distance function, quotient real equality, trichotomy, selected nearest points, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[SignedDistance NameCert obligations]
\label{thm:signed-distance-namecert-obligations}
For every accepted $\SignedDistanceUp$ carrier
$$
S=(M,L,A,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\SignedDistanceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed metric distance row, located-source row, signed-side apartness row, dyadic budget, regular rational readback, real seal, transport, replay, provenance, and local naming rows;
\item located-boundary stability, requiring every transported or replayed signed-distance request to read the same metric row $M$, located-source row $L$, signed-side row $A$, dyadic budget $D$, and regular readback $R$ before exposing the real seal $E$;
\item signed-budget exactness, requiring the sign threshold and rational tolerance in $D$ to be the budget read both by the metric comparison in $M$ and by the signed-side separation row $A$;
\item real-seal nonescape, requiring every real-facing or completion-facing consumer to pass through $M,L,A,D,R,E$ and to receive no host distance function, quotient real representative, selected nearest point, trichotomy, or ambient completeness theorem;
\item ledger refusal, requiring $H,C,P,N$ to transport, replay, source, and name only the displayed rows, with no Lean verification or bridge credential.
\end{enumerate}
No signed-distance NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:signed-distance-carrier}. The packet displays exactly the metric distance row, the located-source row, the signed-side apartness row, the dyadic budget, the regular readback, the real seal, and the four structural rows.

Located-boundary stability is componentwise. A transported or replayed signed-distance request keeps the same metric row $M$ and located row $L$, so the boundary being queried cannot be replaced by a host subset or by an unrecorded completion object.

Signed-budget exactness is the shared role of $A$ and $D$. The signed-side row names the finite separation evidence, while the dyadic row fixes the tolerance and sign threshold read by the metric comparison and the regular rational observation.

For real-seal nonescape, the seal $E$ appears only after $M,L,A,D,R$ have been displayed. A real-facing consumer therefore receives a finite signed-distance route rather than a host distance function, quotient representative, nearest-point selector, trichotomy decision, or completeness theorem.

Finally, $H,C,P,N$ only transport, replay, source, and name the carrier rows. Since the packet contains no Lean verification row and no bridge credential, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[SignedDistance located boundary]
\label{thm:signed-distance-located-boundary}
Every accepted $\SignedDistanceUp$ carrier
$$
S=(M,L,A,D,R,E,H,C,P,N)
$$
binds its signed-distance read to the located boundary named by $L$. Any consumer that reads the sign or magnitude surface must first expose the $\MetricSpaceUp$ distance row $M$, the $\LocatedSpaceUp$ source row $L$, the $\ApartnessRealUp$ signed-side row $A$, the $\DyadicRatCoreUp$ budget row $D$, and the $\RegSeqRatUp$ readback row $R$. The exported boundary information is only this finite route and not a selected nearest point, a decidable side choice, a quotient real equality, or an ambient completeness claim.
\end{theorem}
\begin{proof}
Start with an accepted packet and project its rows from \autoref{def:signed-distance-carrier}. The only boundary-bearing coordinate is the located-source row $L$, while the metric and signed-side observations are carried by $M$ and $A$.

The consumer route then opens the dyadic budget $D$. This budget fixes the finite tolerance and sign threshold used by both the metric comparison and the signed-side separation row.

The regular readback $R$ is the only row that exposes rational observations downstream. It links the displayed metric and signed-side data to the terminal real seal, so no host comparison or hidden side decision can be inserted between the boundary row and the readback.

Thus every sign or magnitude read is bound to the displayed located boundary. The excluded nearest-point, decidable-side, quotient-equality, and ambient-completeness data cannot be exported because they do not occur in the carrier.
\end{proof}

\begin{theorem}[SignedDistance Real seal nonescape]
\label{thm:signed-distance-real-seal-nonescape}
Every $\RealUp$-facing read of an accepted $\SignedDistanceUp$ carrier
$$
S=(M,L,A,D,R,E,H,C,P,N)
$$
factors through the displayed route
$$
M,L,A,D,R \longmapsto E .
$$
The factorization exports the regular signed-distance seal $E$ only after the metric row, located-source row, signed-side row, dyadic budget, and regular readback have been displayed, and it exports no host real-valued distance function, quotient real equality, trichotomy, selected nearest point, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Project the accepted carrier. The real-facing coordinate is the seal $E$, and its replay row $C$ displays a route whose source rows are $M,L,A,D,R$.

The metric row $M$ supplies only finite distance observations, while the located row $L$ supplies only the displayed boundary source. The signed-side row $A$ and dyadic budget $D$ then fix the finite sign and tolerance data read by the regular row $R$.

Only after these rows are visible can the route reach $E$. Componentwise transport in $H$, replay in $C$, provenance in $P$, and the local row $N$ preserve the same order under classification.

Therefore the $\RealUp$-facing read factors through the displayed finite route. The excluded host function, quotient equality, trichotomy, nearest-point, completeness, Lean-verification, and bridge data have no carrier coordinate and cannot escape through the seal.
\end{proof}

\closureat{SignedDistanceUp}{seedStr}

\begin{closurestatus}{\SignedDistanceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:signed-distance-carrier}, \autoref{thm:signed-distance-namecert-obligations}, \autoref{thm:signed-distance-located-boundary}, and \autoref{thm:signed-distance-real-seal-nonescape} seed the finite signed-distance route from metric and located boundary data through apartness, dyadic budget, and regular readback rows to the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host distance functions, quotient real equality, trichotomy, selected nearest points, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-boundary stability, signed-budget exactness, real-seal nonescape, and ledger refusal for BEDC.Derived.SignedDistanceUp.}
  \constructivestory{A $\SignedDistanceUp$ packet is generated from a metric distance row, a located-source row, an ApartnessReal signed-side row, a DyadicRatCore budget, a RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
