\chapter{A Concrete Naming Certificate for $\HolderInequalityUp$}
\label{ch:concrete-instances-holder-inequality-namecert}
\origin{human}

Following Hardy--Littlewood--Polya and the finite-sum form of classical real analysis, the $\HolderInequalityUp$ packet records the BEDC route by which Holder inequality reads over displayed finite real-vector and finite-series windows become available to downstream consumers. It sits after the square-form inequality route of \autoref{ch:concrete-instances-cauchy-schwarz-real-namecert}, the partial-sum and tail surface of \autoref{ch:concrete-instances-realseries-namecert}, and the apartness-from-zero positivity boundary of \autoref{ch:concrete-instances-positivereal-namecert}. The packet is a finite real-analysis inequality certificate; it is not a host real function-space theorem, a quotient stream equality, a selected infinite sum, a countable-choice principle, ambient $\RealUp$ completeness, or bridge checking.

\begin{definition}[Holder inequality carrier]\label{def:holder-inequality-carrier}
A $\HolderInequalityUp$ carrier is a finite $\BHist$ packet
$$
K=(X,Y,W,A,B,C,D,E,F,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two finite real-vector or finite-series windows. Each inspected coordinate is exposed through a $\RealUp$ endpoint seal and the finite readback rows already used by the surrounding real-analysis packets.
\item $W$ is the shared finite observation window. It records the displayed index set, the term reads for $X$ and $Y$, and the product-row reads used by the inequality-facing consumer.
\item $A$ is the conjugate positive exponent ledger. It records the positive exponent rows $p$ and $q$, the finite certificate that they are conjugate, and the positivity evidence needed to use them as Holder weights.
\item $B$ is the $\PositiveRealUp$ boundary for every positive exponent, weight, and norm-like scalar consumed by the packet.
\item $C$ is the $\CauchySchwarzRealUp$ finite inequality route used for the square-case handoff and for the displayed two-row comparison subpacket.
\item $D$ is the $\RealSeriesUp$ finite partial-sum route. It exposes only the selected finite sums of coordinate powers, products, and comparison rows visible in $W$.
\item $E$ is the dyadic tolerance budget. It stores the finite comparison radii, product slack, exponent-ledger tolerances, and endpoint rounding rows.
\item $F$ is the terminal $\RealUp$ endpoint seal for the displayed Holder inequality read.
\item $H$ records componentwise $\hsame$ transport for the vector or series windows, conjugate exponent ledger, positivity boundary, Cauchy--Schwarz route, finite-series route, dyadic budget, endpoint seal, replay, provenance, and local naming rows.
\item $T$ records displayed $\Cont$ replay from any finite coordinate request through $W,A,B,C,D,E,F$ and back to the public inequality boundary.
\item $P$ is the $\Pkg$ provenance over $\HolderInequalityUp$, $\CauchySchwarzRealUp$, $\RealSeriesUp$, $\PositiveRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HolderInequalityUp}$ row.
\end{enumerate}
The carrier predicate is exactly the assertion that these rows form one finite Holder inequality packet. It has no coordinate for a host real function space, quotient equality of streams, selected infinite sums, countable choice, ambient $\RealUp$ completeness, or a standard bridge.
\end{definition}

\begin{theorem}[Holder inequality NameCert obligations]\label{thm:holder-inequality-namecert-obligations}
For every accepted $\HolderInequalityUp$ carrier $K=(X,Y,W,A,B,C,D,E,F,H,T,P,N)$, the local $\NameCert_{\HolderInequalityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two displayed finite windows, shared observation window, conjugate positive exponent ledger, positivity boundary, Cauchy--Schwarz route, finite-series route, dyadic tolerance budget, endpoint seal, transport, replay, provenance, and local naming rows;
\item classifier transport, requiring $H$ and $T$ to preserve the same finite windows, exponent rows, positive scalar evidence, square-case comparison route, finite partial-sum rows, tolerance ledger, endpoint seal, and local naming row componentwise;
\item conjugate-exponent exactness, requiring the positive exponent data in $A$ and $B$ to be the only source of the Holder exponent relation exported by the packet;
\item finite-sum coverage, requiring every product, power, norm-like scalar, and comparison read to pass through $W,C,D,E,F$ before the certificate row is available;
\item ledger non-escape, excluding host real function spaces, quotient stream equality, selected infinite sums, countable choice, ambient $\RealUp$ completeness, hidden order principles, and bridge checking.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The analytic coordinates are the two finite windows $X,Y$, the shared observation row $W$, the exponent ledger $A$, the positivity boundary $B$, the Cauchy--Schwarz route $C$, the real-series route $D$, the dyadic budget $E$, and the endpoint seal $F$.

Carrier admission is exactly admission of those displayed rows together with $H,T,P,N$. The certificate has no additional coordinate from which a host real function-space object, quotient representative, infinite sum, countable-choice selector, or ambient completeness witness could be recovered.

Classifier transport is componentwise. The $\hsame$ rows in $H$ keep the windows, exponent rows, positivity evidence, square-case route, finite-series rows, tolerance budget, and endpoint seal aligned, while $T$ replays the same displayed finite route for later consumers.

Conjugate-exponent exactness follows because $A$ is the only exponent-ledger coordinate and $B$ is the only positive-real boundary coordinate available to it. Thus the exported exponent relation is the displayed positive finite ledger, not a host algebraic theorem imported from outside the packet.

Finite-sum coverage is forced by the carrier order. Every product, power, norm-like scalar, and comparison read must pass through the finite windows, the square-case and series routes, the dyadic tolerance budget, and the endpoint seal before $N$ can name the packet.

The non-escape clause is immediate from the carrier surface. None of host real function spaces, quotient stream equality, selected infinite sums, countable choice, ambient $\RealUp$ completeness, hidden order principles, or bridge checking is a coordinate of $K$.
\end{proof}

\begin{theorem}[Holder inequality finite-sum route]\label{thm:holder-inequality-finite-sum-route}
For every accepted $\HolderInequalityUp$ carrier $K=(X,Y,W,A,B,C,D,E,F,H,T,P,N)$, every inequality-facing read factors through the displayed finite route
$$
X,Y,W \longmapsto A,B \longmapsto C,D \longmapsto E \longmapsto F \longmapsto H,T,P,N .
$$
Consequently the read uses only finite vector or series windows, conjugate positive exponent ledgers, $\PositiveRealUp$ positivity rows, the square-case comparison route supplied by $\CauchySchwarzRealUp$, the partial-sum route supplied by $\RealSeriesUp$, a dyadic tolerance budget, and a terminal $\RealUp$ endpoint seal. It supplies no host real function space, quotient stream equality, selected infinite sum, countable choice, ambient $\RealUp$ completeness, or bridge-checked standard theorem.
\end{theorem}
\begin{proof}
Start from an accepted carrier. The only displayed coordinate data are $X,Y,W$, so every product, power, and scalar comparison request begins in the finite windows.

The exponent information is then fixed by $A$ and $B$. The packet can use the conjugate positive exponent relation only through the displayed ledger and its positive-real boundary.

The inequality route is fixed by $C,D,E,F$. The square-case comparison is read through the $\CauchySchwarzRealUp$ row, the finite partial sums are read through the $\RealSeriesUp$ row, the dyadic tolerance budget records the comparison slack, and the endpoint row seals the resulting $\RealUp$ inequality read.

The rows $H,T,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for a host real function space, quotient stream equality, selected infinite sum, countable choice, ambient $\RealUp$ completeness, or bridge checking, every inequality-facing consumer receives only the displayed finite-sum route.
\end{proof}

\falsifiablePrediction{Every $\HolderInequalityUp$ inequality-facing read factors through finite vector or series windows, a conjugate positive exponent ledger, PositiveRealUp positivity rows, CauchySchwarzRealUp square-case routing, RealSeriesUp partial-sum routing, a dyadic tolerance budget, a RealUp endpoint seal, transport, replay, provenance, and local naming.}

\independenceWitness{cauchy-schwarz-real, realseries, positivereal: $\HolderInequalityUp$ is not bijective to any listed sibling because it jointly carries finite windows, conjugate exponent evidence, positive-real rows, square-case comparison routing, finite partial-sum routing, dyadic tolerance accounting, endpoint sealing, transport, replay, provenance, and local naming.}

\closureat{HolderInequalityUp}{seedStr}

\begin{closurestatus}{\HolderInequalityUp}
  \constructivestory{A $\HolderInequalityUp$ packet is generated from two finite real-vector or finite-series windows, a shared observation window, a conjugate positive exponent ledger, PositiveRealUp positivity rows, CauchySchwarzRealUp and RealSeriesUp finite routes, a dyadic tolerance budget, a RealUp endpoint seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:holder-inequality-carrier}, \autoref{thm:holder-inequality-namecert-obligations}, and \autoref{thm:holder-inequality-finite-sum-route} seed the finite Holder inequality boundary for displayed RealUp finite-vector and finite-series windows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real function spaces, quotient stream equality, selected infinite sums, countable choice, ambient $\RealUp$ completeness, hidden order principles, bridge checking, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, conjugate-exponent exactness, finite-sum coverage, ledger non-escape, and TasteGate field faithfulness for BEDC.Derived.HolderInequalityUp.}
\end{closurestatus}
