\chapter{A Concrete Naming Certificate for $\RegularCauchyReindexInvarianceUp$}
\label{ch:concrete-instances-regular-cauchy-reindex-invariance-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyReindexInvarianceUp$ packet records the finite route by which a regular Cauchy rational name is read unchanged through a displayed monotone cofinal reindexing and a finite tail shift before any completion-facing consumer reaches the real-name seal. It sits after the cofinal route surface of \autoref{ch:concrete-instances-cauchy-reindexing-namecert}, the tail-invariance route of \autoref{ch:concrete-instances-regular-cauchy-shift-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet makes reindex invariance visible as BEDC NameCert data rather than as quotient stream equality, selected limits, countable choice, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Regular-Cauchy reindex-invariance carrier]
\label{def:regular-cauchy-reindex-invariance-carrier}
A $\RegularCauchyReindexInvarianceUp$ carrier is a finite $\BHist$ packet
$$
J=(Q,I,T,S,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the source $\RegSeqRatUp$ row whose regular rational Cauchy readback supplies the inspected values and regularity budget.
\item $I$ is the accepted $\CauchyReindexingUp$ route. It displays a monotone cofinal index map and the finite evidence that every target request is sent to a source request still visible to the source row.
\item $T$ is the $\RegularCauchyShiftUp$ tail route. It records the finite prefix shift needed to align the cofinal route with the retained regular Cauchy windows.
\item $S$ is the $\StreamNameUp$ window ledger opened for the source row, the reindexed route, the shifted tail route, and the seal-facing request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger shared by the source row, reindexed windows, tail-shift windows, regular rational readback, and terminal seal.
\item $R$ is the $\RegSeqRatUp$ readback row obtained only after $Q,I,T,S,D$ have been displayed.
\item $E$ is the $\RealUp$ seal row exposed only after the reindex route, tail route, windows, dyadic ledger, and regular rational readback have been consumed.
\item $H$ records componentwise $\hsame$ transport for the source row, reindex route, tail route, stream windows, dyadic tolerance ledger, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-facing request through
$$
Q,I,T,S,D,R \longmapsto E,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyReindexInvarianceUp$, $\CauchyReindexingUp$, $\RegularCauchyShiftUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyReindexInvarianceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,I,T,S,D,R,E,H,C,P,N$. It has no coordinate for quotient streams, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular-Cauchy reindex-invariance NameCert obligations]
\label{thm:regular-cauchy-reindex-invariance-namecert-obligations}
For every accepted $\RegularCauchyReindexInvarianceUp$ carrier
$$
J=(Q,I,T,S,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyReindexInvarianceUp}$ surface consists exactly of six finite obligation rows:
\begin{enumerate}
\item carrier admission for the source regular Cauchy row, cofinal reindex route, tail-shift route, stream-window ledger, dyadic tolerance ledger, regular rational readback, real seal, componentwise transport, continuation replay, provenance, and local naming rows;
\item monotone-cofinal route preservation, requiring every seal-facing request to pass through the displayed $\CauchyReindexingUp$ row $I$ before any source observation is inspected;
\item tail-shift compatibility, requiring the reindexed request to pass through the displayed $\RegularCauchyShiftUp$ row $T$ when a finite prefix is discarded;
\item dyadic tolerance preservation, requiring $D$ to be the same tolerance ledger consumed by $Q,I,T,S,R$ and the seal row $E$;
\item $\RealUp$ seal handoff, requiring the seal row $E$ to be downstream of $I,T,S,D,R$ and never directly exposed from the source row alone;
\item ledger nonescape, requiring $H,C,P,N$ to transport, replay, source, and name only the displayed finite route.
\end{enumerate}
No NameCert obligation is stored outside these rows, and none exports quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:regular-cauchy-reindex-invariance-carrier}. The visible analytic rows are exactly the source regular Cauchy row $Q$, cofinal reindex route $I$, tail-shift route $T$, stream windows $S$, dyadic ledger $D$, readback $R$, and real seal $E$.

Monotone-cofinal route preservation is read from $I$. A seal-facing request cannot inspect a source observation until the displayed reindex route supplies the monotone cofinal source index and its finite admission evidence.

Tail-shift compatibility is read from $T$. If the cofinal route discards a finite prefix, the packet uses the already displayed $\RegularCauchyShiftUp$ row rather than an external tail selector.

Tolerance preservation is the projection to $D$. The source row, reindex route, tail route, stream windows, readback, and real seal all consume that same dyadic ledger, so no detached modulus can alter the reindexed read.

The seal handoff is the projection to $E$ together with the replay row $C$. Since $E$ appears only downstream of $I,T,S,D,R$, every real-facing read follows the displayed route before it reaches the terminal seal.

Finally $H,C,P,N$ are structural rows. They preserve, replay, source, and name only the admitted packet, leaving no coordinate from which quotient streams, selected limits, countable choice, host real equality, trichotomy, ambient completeness, Lean verification, or bridge data could be read.
\end{proof}

\begin{theorem}[Regular-Cauchy reindex-invariance Real seal handoff]
\label{thm:regular-cauchy-reindex-invariance-real-seal-handoff}
Let
$$
J=(Q,I,T,S,D,R,E,H,C,P,N)
$$
be an accepted $\RegularCauchyReindexInvarianceUp$ carrier. Every $\RealUp$ read and every completion-facing read from $J$ factors first through the $\CauchyReindexingUp$ row $I$ and the $\RegularCauchyShiftUp$ row $T$ before the $\RegSeqRatUp$ readback row $R$ and the $\RealUp$ seal row $E$ are consumed. Consequently the packet exposes reindex invariance only as the displayed route
$$
Q,I,T,S,D,R \longmapsto E,H,C,P,N
$$
and exports no quotient stream, selected limit, countable choice principle, host real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$ or completion-facing consumer request. The carrier exposes the seal row $E$ only downstream of the reindex, tail, window, tolerance, and readback rows, so the consumer must first read $I$ and $T$ before any seal-facing route is available.

The reindex step is finite data. The row $I$ displays the monotone cofinal source request used for the consumer's target request, and the row $S$ records the finite windows in which that request is observed.

The tail step is likewise finite. The row $T$ supplies the $\RegularCauchyShiftUp$ route that accounts for the discarded prefix before the readback row $R$ is consumed.

The dyadic and readback rows then determine the seal-facing observation. The ledger $D$ is shared by the source, reindex, tail, window, readback, and seal rows, while $R$ is the only $\RegSeqRatUp$ handoff row available to the consumer.

The structural rows close the route. Transport, replay, provenance, and local naming preserve only $Q,I,T,S,D,R,E$, so the consumer has no coordinate for quotient streams, selected limits, countable choice, host real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{proof}

\closureat{RegularCauchyReindexInvarianceUp}{seedStr}

\begin{closurestatus}{\RegularCauchyReindexInvarianceUp}
  \constructivestory{A $\RegularCauchyReindexInvarianceUp$ packet is generated from a RegSeqRat source row, a CauchyReindexing monotone cofinal route, a RegularCauchyShift tail route, StreamName windows, a DyadicRatCore tolerance ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-reindex-invariance-carrier}, \autoref{thm:regular-cauchy-reindex-invariance-namecert-obligations}, and \autoref{thm:regular-cauchy-reindex-invariance-real-seal-handoff} seed the finite route by which regular Cauchy rational names are read through displayed monotone cofinal reindexing and finite tail shifts before RegSeqRat readback and RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, monotone-cofinal route preservation, tail-shift compatibility, dyadic tolerance preservation, Real-seal handoff, and ledger nonescape for BEDC.Derived.RegularCauchyReindexInvarianceUp.}
\end{closurestatus}
