\chapter{A Concrete Naming Certificate for $\GaussTestUp$}
\label{ch:concrete-instances-gauss-test-namecert}
\origin{human}

Following Gauss' positive-series test as presented by Knopp, the $\GaussTestUp$ packet records the finite first-order adjacent-quotient defect route by which a positive $\RealSeriesUp$ source exposes a displayed comparison-test tail handoff. It refines the partial-sum windows and tail thresholds of \autoref{ch:concrete-instances-realseries-namecert}, sits beside the quotient and comparison surfaces of \autoref{ch:concrete-instances-regular-cauchy-ratio-test-namecert} and \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}, shares neighboring defect rows with \autoref{ch:concrete-instances-raabe-duhamel-test-namecert} and \autoref{ch:concrete-instances-kummer-test-namecert}, and exports endpoints only through \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names finite Gauss-test evidence only through displayed source windows, adjacent quotient windows, unary first-order defect coefficients, dyadic margins, comparison routing, regular rational readback, and terminal Real sealing; it does not import a host infinite sum, selected limit, quotient series equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Gauss test carrier]\label{def:gauss-test-carrier}
A $\GaussTestUp$ carrier is a finite $\BHist$ packet
$$
G=(S,Q,F,D,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\RealSeriesUp$ row. It exposes only positive-term windows, partial-sum windows, and tail-threshold requests already visible at the real-series boundary.
\item $Q$ is the adjacent quotient-window row. It records the inspected neighboring-term ratios and the finite index window on which those quotients are read.
\item $F$ is the unary first-order defect coefficient row. It records the displayed coefficient data for the Gauss expansion of the adjacent quotient defect on the inspected tail window.
\item $D$ is the $\DyadicRatCoreUp$ margin row. It records the rational error margins, threshold witnesses, and finite inequality budgets used to compare the displayed defect coefficient with the required tail bound.
\item $T$ is the comparison-test handoff row. It routes $S,Q,F,D$ into the finite majorant or minorant surface consumed by $\RegularCauchyComparisonTestUp$.
\item $R$ is the $\RegSeqRatUp$ readback row reached only after the comparison-test handoff and finite stream windows have been displayed.
\item $E$ is the terminal $\RealUp$ seal for endpoint-facing consumers.
\item $H$ stores componentwise $\hsame$ transport for the source, quotient-window, defect-coefficient, margin, comparison, readback, seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from each tail request through $S,Q,F,D,T,R,E$.
\item $P$ is the $\Pkg$ provenance over $\GaussTestUp$, $\RealSeriesUp$, $\RegularCauchyRatioTestUp$, $\RegularCauchyComparisonTestUp$, $\RaabeDuhamelTestUp$, $\KummerTestUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\GaussTestUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,Q,F,D,T,R,E,H,C,P,N$. It has no coordinate for a host infinite sum, selected limit, quotient series equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Gauss test NameCert obligations]\label{thm:gauss-test-namecert-obligations}
For every accepted $\GaussTestUp$ carrier
$$
G=(S,Q,F,D,T,R,E,H,C,P,N),
$$
the local $\NameCert_{\GaussTestUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source $\RealSeriesUp$ windows, adjacent quotient windows, unary first-order defect coefficient row, dyadic error margins, comparison-test handoff, $\RegSeqRatUp$ readback, $\RealUp$ seal, transport, replay, provenance, and local naming rows;
\item quotient-window exactness, requiring every quotient read used by the Gauss defect to be read from the displayed neighboring positive-term windows in $S$ and $Q$;
\item defect-row stability, requiring the coefficient row $F$ and the error margins in $D$ to remain fixed under the accepted tail request and under componentwise $\hsame$ transport;
\item comparison routing, requiring $T$ to be the only row that turns the Gauss defect data into a convergence-test handoff;
\item $\RegSeqRatUp$ and $\RealUp$ seal nonescape, requiring endpoint-facing data to pass through $R$ and then $E$ only after $S,Q,F,D,T$ have been displayed;
\item transport, replay, provenance, and naming discipline, requiring $H,C,P,N$ to transport, replay, source, and name exactly the displayed finite route.
\end{enumerate}
No Gauss-test obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier $G=(S,Q,F,D,T,R,E,H,C,P,N)$. The carrier inventory already displays the real-series source, quotient windows, first-order defect coefficient row, dyadic margins, comparison handoff, readback, seal, transport, replay, provenance, and local name.

The quotient and defect clauses are finite. The source row $S$ gives only inspected positive-term and partial-sum windows, while $Q$ records neighboring-term quotients on the same tail window. The coefficient row $F$ stores the unary first-order defect data, and $D$ stores the rational margins and thresholds attached to that read.

The comparison handoff is forced through $T$. Before $T$ appears, the packet has displayed only source, quotient, defect, and margin rows; after $T$ appears, the endpoint route may proceed to the regular rational readback $R$ and terminal seal $E$.

Finally $H,C,P,N$ preserve and name this same route. Since the carrier has no excluded coordinate for host summation, selected limits, quotient series equality, choice, trichotomy, ambient real completeness, Lean verification, or bridge checking, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Gauss test tail handoff]\label{thm:gauss-test-tail-handoff}
Every endpoint-facing read of an accepted $\GaussTestUp$ carrier factors through
$$
\RealSeriesUp,\ \RegularCauchyRatioTestUp,\ \RegularCauchyComparisonTestUp,\ \RaabeDuhamelTestUp,\ \KummerTestUp,\ \DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
Concretely, the read consumes the source $\RealSeriesUp$ windows, the adjacent quotient surface shared with $\RegularCauchyRatioTestUp$, the neighboring first-order defect discipline visible beside $\RaabeDuhamelTestUp$ and $\KummerTestUp$, the dyadic and stream display rows, and the $\RegularCauchyComparisonTestUp$ handoff before it reaches $\RegSeqRatUp$ and $\RealUp$.
\end{theorem}
\begin{proof}
Begin with an endpoint-facing read of an accepted carrier. By \autoref{def:gauss-test-carrier}, the only source data available at the start are the $\RealSeriesUp$ windows in $S$ and the adjacent quotient windows in $Q$.

The Gauss-specific defect data are then read from $F$ and $D$. These rows display the unary first-order coefficient data, the rational margins, and the tail threshold needed for the finite comparison request.

The neighboring tests are reference faces for the same quotient-defect lattice. The $\RegularCauchyRatioTestUp$ surface supplies the adjacent quotient discipline, while $\RaabeDuhamelTestUp$ and $\KummerTestUp$ identify the nearby defect rows. The accepted $\GaussTestUp$ route still reaches endpoints only through the comparison handoff $T$.

After $T$ is displayed, the route proceeds through the finite $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ margins, the $\RegSeqRatUp$ readback row $R$, and the terminal $\RealUp$ seal $E$. The transport, replay, provenance, and naming rows keep the same route, so no host infinite sum, selected limit, quotient series equality, countable choice, trichotomy, or ambient $\RealUp$ completeness can enter.
\end{proof}

\closureat{GaussTestUp}{seedStr}

\begin{closurestatus}{\GaussTestUp}
  \constructivestory{A $\GaussTestUp$ packet is generated from source RealSeries windows, adjacent quotient windows, a unary first-order defect coefficient row, DyadicRatCore error margins, a RegularCauchyComparisonTest handoff, StreamName display rows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:gauss-test-carrier}, \autoref{thm:gauss-test-namecert-obligations}, and \autoref{thm:gauss-test-tail-handoff} seed the finite Gauss positive-series test boundary over displayed source series, quotient, first-order defect, comparison, $\RegSeqRatUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, selected limits, quotient series equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean theorems for carrier admission, quotient-window exactness, defect-row stability, comparison routing, $\RegSeqRatUp$ and $\RealUp$ seal nonescape, transport, replay, provenance, and local naming discipline for BEDC.Derived.GaussTestUp.}
\end{closurestatus}
