\chapter{A Concrete Naming Certificate for $\CauchyRealLocatedOrderTestUp$}
\label{ch:concrete-instances-cauchy-real-located-order-test-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CauchyRealLocatedOrderTestUp$ packet names the finite located-order test by which two displayed real names are compared through regular Cauchy readbacks, shared windows, dyadic tolerances, positive-gap evidence when present, and located-interval context before any Real-facing consumer reads the result. It sits after the comparison-test surface of \autoref{ch:concrete-instances-regular-cauchy-comparison-test-namecert}, the constructive order surface of \autoref{ch:concrete-instances-cauchy-real-order-namecert}, the positive-separation surface of \autoref{ch:concrete-instances-apartnessreal-namecert}, the located interval context of \autoref{ch:concrete-instances-located-real-interval-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet is a finite Bishop-style located order test for $\RealUp$ names; it is not host trichotomy, quotient real equality, a representative selector, countable choice, or ambient real completeness.

\begin{definition}[Cauchy real located order test carrier]
\label{def:cauchy-real-located-order-test-carrier}
A $\CauchyRealLocatedOrderTestUp$ carrier is a finite $\BHist$ packet
$$
T=(X,Y,W,D,Q,O,A,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ and $Y$ are the two source rows. Each row is read as a displayed $\RegSeqRatUp$ packet and then sealed as a $\RealUp$ name before any located-order verdict is exported.
\item $W$ is the shared $\StreamNameUp$ window family. It records the finite observation lengths, synchronised cuts, endpoint readbacks, and comparison windows inspected for both source rows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance budget. It records the requested dyadic scale, positive gap threshold, sign slack, and exhaustion ledger used by the comparison and locatedness rows.
\item $Q$ is the $\RegularCauchyComparisonTestUp$ row. It tests the two regular Cauchy readbacks on the shared windows and dyadic budget before the terminal real-name seals are consumed.
\item $O$ is the $\CauchyRealOrderUp$ row. It stores the oriented order verdict as a finite consequence of $X,Y,W,D,Q$ and does not supply host trichotomy.
\item $A$ is an $\ApartnessRealUp$ positive-gap row when the displayed windows and dyadic budget separate the two real names.
\item $L$ is the $\LocatedRealIntervalUp$ context row. It records the interval enclosure and locatedness data in which the order test is read.
\item $H$ records componentwise $\hsame$ transport for the two source rows, shared windows, dyadic budget, comparison row, order row, positive-gap row when present, located-interval row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each located-order request through $W,D,Q,O,A,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyRealLocatedOrderTestUp$, $\RegularCauchyComparisonTestUp$, $\CauchyRealOrderUp$, $\ApartnessRealUp$, $\LocatedRealIntervalUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyRealLocatedOrderTestUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these twelve rows form one finite located-order test packet. It has no coordinate for host trichotomy, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Cauchy real located order test NameCert obligations]
\label{thm:cauchy-real-located-order-test-namecert-obligations}
For every accepted $\CauchyRealLocatedOrderTestUp$ carrier $T=(X,Y,W,D,Q,O,A,L,H,C,P,N)$, the local $\NameCert_{\CauchyRealLocatedOrderTestUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two regular-rational source rows, terminal real-name seals, shared stream windows, dyadic tolerance budget, comparison-test row, order row, positive-gap row when present, located-interval context row, transport, replay, provenance, and local naming row;
\item classifier exactness, requiring accepted packets to compare only the displayed $X,Y,W,D,Q,O,A,L,H,C,P,N$ coordinates;
\item regular Cauchy comparison readback, requiring $Q$ to inspect the two source rows through the shared windows $W$ and dyadic budget $D$ before the order row is read;
\item located order compatibility, requiring $O$ to export an oriented verdict only inside the located interval context $L$ and only after the comparison-test route has been displayed;
\item positive-gap visibility, requiring every separating verdict to display its $\ApartnessRealUp$ row $A$ as finite dyadic gap evidence over the same $W$ and $D$;
\item nonseparating visibility, requiring every nonseparating read to record the exhausted windows and dyadic slack rather than a quotient equality proof;
\item transport and replay stability, requiring $H$ and $C$ to preserve the source, window, tolerance, comparison, order, apartness, located-context, provenance, and local naming rows componentwise;
\item ledger exhaustion, excluding host trichotomy, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
No located-order test obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier $T=(X,Y,W,D,Q,O,A,L,H,C,P,N)$. The projection exposes exactly the two source rows, common window family, dyadic tolerance budget, comparison row, order row, positive-gap row when present, located-interval context row, and structural rows.

The comparison route is finite. The source rows $X$ and $Y$ are inspected through the shared windows $W$, and the dyadic budget $D$ supplies the scale and slack at which the comparison-test row $Q$ is allowed to read them.

The order and locatedness rows are downstream of this comparison. The row $O$ records only the oriented verdict produced by the displayed comparison route, while $L$ records the interval context in which the verdict is meaningful.

Positive and nonseparating reads use the same ledger. When a positive gap is present, $A$ displays the $\ApartnessRealUp$ separation row. When the gap is not displayed at the requested scale, the packet records the exhausted finite windows and slack; it does not replace that record by quotient equality.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since none of the carrier coordinates stores a host trichotomy, quotient equality, representative selector, choice schedule, completeness datum, Lean theorem, or bridge, no further local obligation can be read from the packet.
\end{proof}

\begin{theorem}[Cauchy real located order test finite decision route]
\label{thm:cauchy-real-located-order-test-finite-decision-route}
Every accepted $\CauchyRealLocatedOrderTestUp$ read factors through the finite route
$$
X,Y \longmapsto W,D \longmapsto Q \longmapsto O,A,L \longmapsto H,C,P,N
$$
before any $\RealUp$ consumer sees the result. Hence the packet exports only the displayed located-order test data, and exports no host trichotomy, quotient real equality, selected representative, countable choice, or $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with an accepted located-order test carrier. The only source coordinates are $X$ and $Y$, and the carrier requires each to pass through regular-rational readback and the terminal real-name seal before the public result is exposed.

The shared windows and tolerance budget come next. The finite windows in $W$ select the inspected stream segments, while the dyadic budget $D$ records the comparison scale, requested gap, sign slack, and exhaustion data.

The comparison-test row $Q$ consumes exactly those rows. The oriented order row $O$, the positive-gap row $A$ when present, and the located-interval context row $L$ are therefore downstream of the displayed comparison route rather than independent Real-level principles.

The structural rows close the route. Componentwise transport in $H$, replay in $C$, provenance in $P$, and local naming in $N$ preserve the same finite packet before a $\RealUp$ consumer can read the verdict. Because the route contains no coordinate for trichotomy, quotient equality, representative selection, countable choice, or completeness, none of those principles is exported.
\end{proof}

\closureat{CauchyRealLocatedOrderTestUp}{seedStr}
\begin{closurestatus}{\CauchyRealLocatedOrderTestUp}
  \constructivestory{A $\CauchyRealLocatedOrderTestUp$ packet is generated from two $\RegSeqRatUp$ source rows sealed as $\RealUp$ names, shared $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ tolerance budget, a $\RegularCauchyComparisonTestUp$ row, a $\CauchyRealOrderUp$ row, an $\ApartnessRealUp$ positive-gap row when present, a $\LocatedRealIntervalUp$ context row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-real-located-order-test-carrier}, \autoref{thm:cauchy-real-located-order-test-namecert-obligations}, and \autoref{thm:cauchy-real-located-order-test-finite-decision-route} seed the finite located-order test boundary over regular Cauchy readbacks, shared stream windows, a dyadic tolerance budget, comparison-test data, order data, apartness data when present, located-interval context, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host trichotomy, quotient real equality, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires a Lean declaration for BEDC.Derived.CauchyRealLocatedOrderTestUp covering the twelve-row carrier, local NameCert obligations, and finite decision route.}
\end{closurestatus}
