\chapter{A Concrete Naming Certificate for $\SilvermanToeplitzUp$}
\label{ch:concrete-instances-silverman-toeplitz-namecert}
\origin{human}

Following Silverman, Toeplitz, and Hardy on regular matrix summability, the $\SilvermanToeplitzUp$ packet records the finite BEDC certificate by which a row-finite inspection of a summability matrix sends a convergent regular real-name sequence to the same $\RealUp$ endpoint. It refines the matrix-window route of \autoref{ch:concrete-instances-toeplitz-lemma-namecert}, contains the Cesaro averaging and convergence special cases of \autoref{ch:concrete-instances-hardy-cesaro-mean-namecert} and \autoref{ch:concrete-instances-cesaro-convergence-namecert}, reads source and transformed rows through \autoref{ch:concrete-instances-regseqrat-namecert}, keeps all rational coefficient budgets inside \autoref{ch:concrete-instances-dyadicratcore-namecert}, and reaches the terminal seal only through \autoref{ch:concrete-instances-real-namecert}. The chapter names the local certificate surface for regular matrices; it does not import a host summability theorem, a completed infinite matrix, quotient equality of real-name streams, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Silverman--Toeplitz carrier]\label{def:silverman-toeplitz-carrier}
A $\SilvermanToeplitzUp$ carrier is a finite $\BHist$ packet
$$
S=(M,B,V,W,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the matrix coefficient-window row, listing the finite rows, finite column windows, coefficient approximants, truncation thresholds, and row-index requests currently inspected.
\item $B$ is the row-sum bound ledger, recording the dyadic bounds used to keep each displayed matrix row uniformly bounded before a transformed read is exposed.
\item $V$ is the column-vanishing ledger, recording for each displayed source tolerance the finite column requests whose coefficients are certified small along sufficiently late matrix rows.
\item $W$ is the source $\StreamNameUp$ window row, listing only the finite input-sequence observations demanded by $M,B,V$.
\item $T$ is the transformed finite-row surface, obtained from the displayed coefficients in $M$, the selected source windows in $W$, and the dyadic budgets in $B,V$.
\item $R$ is the $\RegSeqRatUp$ readback row for both the source windows used by the regularity argument and the transformed rows exposed by $T$.
\item $E$ is the $\RealUp$ seal reached only after the matrix windows, bounded-row ledger, column-vanishing ledger, source windows, transformed finite rows, and regular readback have been displayed.
\item $H$ stores componentwise $\hsame$ transport for matrix windows, row-sum bounds, column-vanishing data, source windows, transformed rows, regular readback, real seals, continuation rows, provenance, and local naming.
\item $C$ stores displayed $\Cont$ replay from matrix-row inspection to source-window selection, from row-sum and column-vanishing ledgers to transformed-row construction, from transformed rows to regular readback, and from regular readback to the real seal.
\item $P$ is the $\Pkg$ provenance over $\SilvermanToeplitzUp$, $\ToeplitzLemmaUp$, $\HardyCesaroMeanUp$, $\CesaroConvergenceUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SilvermanToeplitzUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,B,V,W,T,R,E,H,C,P,N$. It has no coordinate for a host summability method, a completed infinite matrix, a selected external limit, quotient equality of real-name streams, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Silverman--Toeplitz NameCert obligations]\label{thm:silverman-toeplitz-namecert-obligations}
For every accepted $\SilvermanToeplitzUp$ carrier $S=(M,B,V,W,T,R,E,H,C,P,N)$, the local $\NameCert_{\SilvermanToeplitzUp}$ surface consists exactly of the following six finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed matrix coefficient windows, row-sum bound ledger, column-vanishing ledger, source windows, transformed finite rows, regular readback, real seal, transport, continuation, provenance, and naming rows;
\item bounded-row exactness, requiring every row-sum bound used by the transform to be read from $B$ after the corresponding coefficient windows in $M$ have been displayed;
\item column-vanishing exactness, requiring every small-column claim to pass through the displayed column ledger $V$ and the same finite matrix-window row $M$;
\item source-to-transform construction, requiring every transformed row to be computed from $M,B,V,W$ before the transformed read reaches $T$;
\item regular readback and real sealing, requiring every completion-facing transformed read to pass through $R$ and then $E$;
\item transport, continuation, provenance, and local naming, requiring $H,C,P,N$ to preserve the same finite route without adding a host summability or ambient completeness coordinate.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:silverman-toeplitz-carrier}. Carrier admission is exactly the displayed inventory $M,B,V,W,T,R,E,H,C,P,N$, so the local certificate has no detached coordinate for an infinite matrix or a host summability method.

The bounded-row and column-vanishing clauses are read from $B$ and $V$ only after the inspected coefficient windows in $M$ have been displayed. The selected input observations are the finite $\StreamNameUp$ windows in $W$, and the transformed finite row $T$ is downstream of those same rows.

The regularity handoff is then forced through $R$, and the endpoint-facing route continues from $R$ to the $\RealUp$ seal $E$. The structural rows $H,C,P,N$ transport, replay, source, and name this route, and none of them contains an additional analytic principle.
\end{proof}

\begin{theorem}[Silverman--Toeplitz regularity route]\label{thm:silverman-toeplitz-regularity-route}
Every accepted $\SilvermanToeplitzUp$ read that claims preservation of a regular real-name limit factors through the finite route
$$
M \longmapsto (B,V) \longmapsto W \longmapsto T \longmapsto R \longmapsto E \longmapsto (H,C,P,N).
$$
The $\ToeplitzLemmaUp$ route supplies the finite matrix-window discipline, the $\HardyCesaroMeanUp$ and $\CesaroConvergenceUp$ rows are admitted as special provenance surfaces, and no consumer can bypass $\RegSeqRatUp$ readback or the $\RealUp$ seal.
\end{theorem}
\begin{proof}
Start with a preservation read from an accepted carrier. The only coefficient data visible to the classifier are the finite windows in $M$, and the regularity hypotheses for the matrix are represented by the row-sum ledger $B$ and the column-vanishing ledger $V$.

The source sequence is then inspected only through $W$. Hence the transformed row cannot be formed before the coefficient, boundedness, vanishing, and source-window data have all been displayed, which forces the route through $T$.

The transformed sequence reaches any regular real-name consumer through $R$, and the real endpoint is visible only through $E$. Provenance may point to the Toeplitz, Hardy--Cesaro, and Cesaro-convergence sibling chapters, but those pointers are package rows in $P$ and do not create a second path around $M,B,V,W,T,R,E$.

Finally, $H,C,P,N$ preserve and name the same route. Since the carrier has no completed matrix, selected external limit, quotient real-name equality, countable choice, or ambient completeness field, the displayed route exhausts the preservation surface.
\end{proof}

\begin{theorem}[Silverman--Toeplitz Real-seal nonescape]\label{thm:silverman-toeplitz-real-seal-nonescape}
For every accepted $\SilvermanToeplitzUp$ carrier, any $\RealUp$ endpoint exported by the regular matrix transform is sealed only after the matrix-window rows, row-sum ledger, column-vanishing ledger, source windows, transformed finite rows, and $\RegSeqRatUp$ readback have been exposed. Consequently the Real seal cannot be used to recover a host summability theorem, a detached infinite matrix, a selected source limit, quotient stream equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
By \autoref{def:silverman-toeplitz-carrier}, the seal row is $E$, and it is downstream of $M,B,V,W,T,R$. Thus an endpoint-facing consumer has already passed through the finite coefficient windows, the two matrix regularity ledgers, the source windows, the transformed row, and the regular readback.

The remaining rows $H,C,P,N$ only transport, replay, source, and name the same packet. They do not store host analytic data, and the classifier has no coordinate for any excluded principle.

Therefore every exported $\RealUp$ endpoint is a seal for the displayed finite BEDC route rather than a route to host summability, detached infinite matrix data, selected limits, quotient stream equality, countable choice, or ambient $\RealUp$ completeness.
\end{proof}

\falsifiablePrediction{Every $\SilvermanToeplitzUp$ preservation read factors through finite matrix coefficient windows, a row-sum bound ledger, a column-vanishing ledger, source StreamName windows, transformed finite rows, RegSeqRat readback, a RealUp seal, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{toeplitzlemma, hardycesaromean, cesaroconvergence, streamname, regseqrat, dyadicratcore, real: $\SilvermanToeplitzUp$ is not bijective to any listed sibling because it jointly carries matrix coefficient windows, row-sum bounds, column-vanishing data, source windows, transformed rows, regular readback, real sealing, transport, continuation, provenance, and local naming.}

\closureat{SilvermanToeplitzUp}{seedStr}

\begin{closurestatus}{\SilvermanToeplitzUp}
  \constructivestory{A $\SilvermanToeplitzUp$ packet is generated from finite matrix coefficient windows, a row-sum bound ledger, a column-vanishing ledger, source StreamName windows, transformed finite rows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:silverman-toeplitz-carrier}, \autoref{thm:silverman-toeplitz-namecert-obligations}, \autoref{thm:silverman-toeplitz-regularity-route}, and \autoref{thm:silverman-toeplitz-real-seal-nonescape} seed the regular matrix summability certificate surface from finite matrix windows to Real-facing seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host summability theorems, completed infinite matrices, selected source limits, quotient equality of real-name streams, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, bounded-row exactness, column-vanishing exactness, source-to-transform construction, regular readback, Real-seal nonescape, transport and provenance, and TasteGate field faithfulness for BEDC.Derived.SilvermanToeplitzUp.}
\end{closurestatus}
