\chapter{A Concrete Naming Certificate for $\SamuelCompletionUp$}
\label{ch:concrete-instances-samuel-completion-namecert}
\origin{human}

Following Samuel on uniform compactification and Bourbaki--Kelley on uniform-space completion, the $\SamuelCompletionUp$ packet records the completion-facing uniform route as finite BEDC data. It sits after the uniform completion surface of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the Cauchy-filter route of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the dense uniform embedding boundary of \autoref{ch:concrete-instances-dense-uniform-embedding-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the L10 uniform-completion handoff without asserting quotient completion, countable choice, a selected limit, host uniform equality, or ambient $\RealUp$ completeness.

\begin{definition}[Samuel completion carrier]
\label{def:samuel-completion-carrier}
A $\SamuelCompletionUp$ carrier is a finite $\BHist$ packet
$$
S=(U,F,D,W,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the finite uniform-entourage row. It records the entourages inspected by the completion request and the refinement edges used to compare them.
\item $F$ is the $\CauchyFilterUp$ row. It records the Cauchy-filter data read through the displayed entourage family.
\item $D$ is the $\DenseUniformEmbeddingUp$ row. It records the dense source embedding, image-window requests, and pullback evidence used before any completion-facing read is exposed.
\item $W$ is the $\StreamNameUp$ finite-window schedule through which dense-source observations and completion-facing requests are inspected.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row attached to the displayed windows and entourage budgets.
\item $A$ is the terminal $\RealUp$ seal, reachable only after the displayed uniform, filter, dense-embedding, stream-window, and regular-rational rows have been read.
\item $H$ records componentwise $\hsame$ transport for entourages, Cauchy-filter rows, dense-embedding rows, stream windows, regular readbacks, real seals, replay data, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
U,D,F,W \longmapsto R \longmapsto A .
$$
\item $P$ is the $\Pkg$ provenance over $\SamuelCompletionUp$, $\UniformCompletionUp$, $\CauchyFilterUp$, $\DenseUniformEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SamuelCompletionUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these ten rows. Its classifier compares accepted packets only through $U,F,D,W,R,A,H,C,P,N$ and has no coordinate for quotient completion, countable choice, selected limits, host uniform equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Samuel completion NameCert obligations]
\label{thm:samuel-completion-namecert-obligations}
For the carrier of \autoref{def:samuel-completion-carrier}, the local $\NameCert_{\SamuelCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the packet $S=(U,F,D,W,R,A,H,C,P,N)$;
\item classifier stability under componentwise $\hsame$ transport of the uniform-entourage row, Cauchy-filter row, dense-embedding row, stream-window schedule, regular rational readback, real seal, replay row, provenance row, and local naming row;
\item displayed $\Cont$ replay of the route from uniform entourages and dense-source windows through Cauchy-filter data to regular rational readback and the terminal real seal;
\item non-escape for every consumer read, requiring the read to remain inside $\UniformCompletionUp$, $\CauchyFilterUp$, $\DenseUniformEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{enumerate}
No obligation is stored in a quotient completion, selected limit, countable-choice schedule, host uniform equality row, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier. Carrier admission is exactly the display of the ten rows $U,F,D,W,R,A,H,C,P,N$, so there is no additional host object to construct.

Classifier stability is componentwise. The $\hsame$ row compares the displayed uniform-entourage, Cauchy-filter, dense-embedding, stream-window, regular-readback, and real-seal coordinates, while the structural rows transport replay, provenance, and local naming over the same coordinates.

The continuation obligation is the displayed route in the carrier. A consumer first reads uniform entourages and dense-source windows, then the Cauchy-filter row, then the regular rational readback, and only then the real seal.

The non-escape clause follows by inspecting the carrier inventory. Since the packet has no coordinate for quotient completion, countable choice, selected limits, host uniform equality, or ambient completeness, no NameCert obligation can export one.
\end{proof}

\begin{theorem}[Samuel completion uniform handoff]
\label{thm:samuel-completion-uniform-handoff}
Every completion-facing read exported by an accepted $\SamuelCompletionUp$ carrier reaches $\RegSeqRatUp$ and $\RealUp$ only after the displayed route through $\UniformCompletionUp$, $\CauchyFilterUp$, and $\DenseUniformEmbeddingUp$ has been read. The handoff route is therefore
$$
U,D,F,W \longmapsto R \longmapsto A \longmapsto H,C,P,N ,
$$
not a quotient-completion carrier, not a selected limit, not a countable-choice schedule, not host uniform equality, and not an ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with an accepted carrier and project its uniform-entourage, Cauchy-filter, dense-embedding, and stream-window rows. These rows are upstream of the regular rational readback row in the displayed route.

The regular readback row $R$ is therefore not available as an isolated real-name source. It is read only after the entourage refinements, dense embedding evidence, Cauchy-filter data, and finite windows have been displayed.

The real seal $A$ is downstream of $R$. Thus every real-facing consumer must traverse the uniform-completion, Cauchy-filter, and dense-embedding route before it can consume a $\RegSeqRatUp$ readback or a terminal $\RealUp$ seal.

Finally the $H,C,P,N$ rows preserve the same route under transport, replay, provenance, and local naming. The excluded host-side principles have no carrier coordinate, so the handoff cannot expose them.
\end{proof}

\closureat{SamuelCompletionUp}{seedStr}

\begin{closurestatus}{\SamuelCompletionUp}
  \constructivestory{A $\SamuelCompletionUp$ packet is generated from finite uniform-entourage rows, CauchyFilterUp data, DenseUniformEmbeddingUp rows, StreamName windows, RegSeqRat readbacks, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:samuel-completion-carrier}, \autoref{thm:samuel-completion-namecert-obligations}, and \autoref{thm:samuel-completion-uniform-handoff} seed the L10 uniform-completion route from finite entourage and dense-embedding data through Cauchy-filter, StreamName, RegSeqRat, Real seal, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, quotient stream equality, selected limits, host uniform equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, displayed continuation replay, uniform handoff, non-escape, provenance, and local naming for BEDC.Derived.SamuelCompletionUp.}
\end{closurestatus}
