\chapter{A Concrete Naming Certificate for $\MonoidalCompletionUp$}
\label{ch:concrete-instances-monoidal-completion-namecert}
\origin{human}

Following Bourbaki and Kelley on completion and product uniformities, and Bishop--Bridges on constructive metric completion, the $\MonoidalCompletionUp$ packet records the finite BEDC surface on which completion is consumed as a product-compatible reflector. It sits over the metric-completion row of \autoref{ch:concrete-instances-metriccompletion-namecert}, the binary product handoff of \autoref{ch:concrete-instances-cauchy-completion-product-namecert}, the functorial completion route of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, and the reflection boundary of \autoref{ch:concrete-instances-completionreflection-namecert}. The chapter names only the finite reflector and coherence rows visible to downstream Real and Completion consumers; it does not construct quotient completions, choose representatives, identify host products, assume countable choice, use open-cover compactness, or import ambient $\RealUp$ completeness.

\begin{definition}[Monoidal completion carrier]
\label{def:monoidal-completion-carrier}
A $\MonoidalCompletionUp$ carrier is a finite $\BHist$ packet
$$
Q=(M,U,V,P,A,S,H,C,G,N)
$$
with the following visible rows:
\begin{enumerate}
\item $M$ is the metric-completion reflector row. It exposes the displayed $\MetricCompletionUp$ source-to-completion route and the reflector-facing boundary inherited from \autoref{ch:concrete-instances-metriccompletion-namecert}.
\item $U$ is the unit row. It records the source-object admission into the completion surface before any product consumer may inspect completed data.
\item $V$ is the counit row. It records the displayed return route for already completed data and keeps that route inside the completion-reflection boundary.
\item $P$ is the binary product row. It is read through the coordinatewise completion product surface of \autoref{ch:concrete-instances-cauchy-completion-product-namecert}, not through host product equality.
\item $A$ is the associativity row. It records that either parenthesization of a finite binary product read uses the same coordinatewise completion, unit, counit, and reflector rows.
\item $S$ is the symmetry row. It records that swapping two displayed coordinates swaps only the finite product rows and their associated transport and replay data.
\item $H$ records componentwise $\hsame$ transport for metric-completion, unit, counit, product, associativity, symmetry, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the product-compatible reflector route from metric completion through unit, counit, binary product, associativity, symmetry, and structural rows.
\item $G$ is the $\Pkg$ provenance over $\MonoidalCompletionUp$, $\MetricCompletionUp$, $\CauchyCompletionProductUp$, $\CauchyCompletionFunctorUp$, $\CompletionReflectionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MonoidalCompletionUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these ten rows. It has no coordinate for quotient completion equality, selected representatives, host product equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, or a host-level symmetric monoidal category.
\end{definition}

\begin{theorem}[Monoidal completion NameCert obligations]
\label{thm:monoidal-completion-namecert-obligations}
For the carrier of \autoref{def:monoidal-completion-carrier}, the local $\NameCert_{\MonoidalCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for $Q=(M,U,V,P,A,S,H,C,G,N)$;
\item reflector compatibility, requiring the metric-completion reflector row $M$, unit row $U$, and counit row $V$ to be consumed through the same completion boundary named in \autoref{ch:concrete-instances-metriccompletion-namecert} and \autoref{ch:concrete-instances-completionreflection-namecert};
\item product compatibility, requiring the binary product row $P$ to factor through the coordinatewise product handoff of \autoref{ch:concrete-instances-cauchy-completion-product-namecert};
\item finite coherence, requiring associativity row $A$ and symmetry row $S$ to compare only displayed product routes and not host product objects;
\item transport and replay stability under componentwise $\hsame$ transport $H$ and displayed $\Cont$ replay $C$;
\item provenance exactness, requiring every consumer read to be sourced by $G$ and locally certified by $N$.
\end{enumerate}
No obligation is stored in a quotient completion, selected representative, host product equality, countable-choice schedule, open-cover compactness theorem, ambient $\RealUp$ completeness theorem, or external monoidal-category structure.
\end{theorem}
\begin{proof}
Carrier admission is projection from the finite packet in \autoref{def:monoidal-completion-carrier}. The only displayed coordinates are the reflector row, unit row, counit row, binary product row, associativity row, symmetry row, transport row, replay row, provenance row, and local naming row.

Reflector compatibility is read through the metric-completion and completion-reflection siblings. The $M,U,V$ rows bind source admission, completed-data return, and reflection boundary before any product-compatible consumer can inspect the route.

Product compatibility is then the coordinatewise handoff supplied by \autoref{ch:concrete-instances-cauchy-completion-product-namecert}. The product row $P$ is a finite route through the displayed coordinate completions and does not add a host product object.

Associativity and symmetry are coherence rows over that finite product route. They compare parenthesized and swapped displays only by reusing the same $M,U,V,P,H,C,G,N$ data, so no quotient equality, selected representative, host product equality, choice principle, compactness theorem, or ambient completeness theorem is available.
\end{proof}

\begin{theorem}[Monoidal completion product reflector handoff]
\label{thm:monoidal-completion-product-reflector-handoff}
Let $Q=(M,U,V,P,A,S,H,C,G,N)$ be an accepted $\MonoidalCompletionUp$ carrier. Every completion-facing product consumer factors through the finite route
$$
M\longmapsto U,V\longmapsto P\longmapsto A,S\longmapsto H,C,G,N .
$$
The handoff uses the metric-completion reflector surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the coordinatewise product surface of \autoref{ch:concrete-instances-cauchy-completion-product-namecert}, the functorial route of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, and the reflection boundary of \autoref{ch:concrete-instances-completionreflection-namecert}; it is not a host product completion and not a quotient completion product.
\end{theorem}
\begin{proof}
Project the accepted carrier. The metric-completion reflector row $M$ supplies the completion-facing source boundary, and the unit and counit rows $U,V$ record the two reflector directions available to consumers.

The binary product row $P$ can be consumed only after those reflector rows are displayed. Its coordinatewise content is the same finite product handoff named by the Cauchy-completion product chapter, while the functorial sibling supplies the route discipline for completion-facing maps.

The associativity and symmetry rows $A,S$ are downstream of $P$. They identify which finite product route is being replayed after a parenthesization or coordinate swap, but they do not identify host product objects.

Finally $H,C,G,N$ preserve the route under transport, replay, provenance, and local certification. Since no further row occurs in $Q$, the consumer obtains exactly the displayed product-compatible reflector handoff and no quotient completion, selected representative, host product equality, choice principle, compactness theorem, or ambient completeness theorem.
\end{proof}

\begin{theorem}[Monoidal completion non-escape]
\label{thm:monoidal-completion-nonescape}
An accepted $\MonoidalCompletionUp$ carrier exports no read outside
$$
(M,U,V,P,A,S,H,C,G,N).
$$
In particular, any product-compatible completion consumer must read metric completion, unit, counit, binary product, associativity, symmetry, componentwise transport, displayed continuation replay, provenance, and local naming evidence from the same finite packet.
\end{theorem}
\begin{proof}
Inspect the carrier inventory in \autoref{def:monoidal-completion-carrier}. Every exported read must be one of the ten displayed rows or a replay of those rows through the local $\NameCert$ surface.

If a consumer omits $M$, it has no metric-completion reflector row. If it omits $U$ or $V$, it has lost one reflector direction. If it omits $P$, it has no binary product handoff. If it omits $A$ or $S$, it has no finite associativity or symmetry comparison for product-compatible reads.

The structural rows are also necessary. Without $H$, the classifier is not stable under componentwise transport; without $C$, the route is not replayed as displayed continuation data; without $G$ and $N$, provenance and local naming are absent.

There is no remaining coordinate. Therefore the packet cannot export quotient completions, selected representatives, host product equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, or an external monoidal-category object.
\end{proof}

\closureat{MonoidalCompletionUp}{seedStr}

\begin{closurestatus}{\MonoidalCompletionUp}
  \constructivestory{A $\MonoidalCompletionUp$ packet is generated from a metric-completion reflector row, unit row, counit row, binary product row, associativity row, symmetry row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:monoidal-completion-carrier}, \autoref{thm:monoidal-completion-namecert-obligations}, \autoref{thm:monoidal-completion-product-reflector-handoff}, and \autoref{thm:monoidal-completion-nonescape} seed the finite product-compatible reflector surface for completion through metric-completion, product, functorial, reflection, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host product equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, or an external monoidal-category structure.}
  \upgradepath{Obligation closure requires checked carrier admission, reflector compatibility, product compatibility, finite associativity and symmetry coherence, transport stability, replay stability, provenance exactness, and non-escape for BEDC.Derived.MonoidalCompletionUp.}
\end{closurestatus}
