\chapter{A Concrete Naming Certificate for $\NormalConvergenceUp$}
\label{ch:concrete-instances-normal-convergence-namecert}
\origin{human}

Following Weierstrass and Bishop--Bridges constructive analysis, the $\NormalConvergenceUp$ packet records the finite normal-convergence route by which a real-series family, an absolute majorant, a displayed M-test tail ledger, and a uniform-limit handoff determine every endpoint-facing series read. It sits after the real-series carrier of \autoref{ch:concrete-instances-realseries-namecert}, the absolute-majorant rows of \autoref{ch:concrete-instances-absolute-convergence-namecert}, the finite majorant tail exactness of \autoref{ch:concrete-instances-weierstrassmtest-namecert}, the uniform endpoint sealing of \autoref{ch:concrete-instances-uniformlimit-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the stream-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies the finite dependency surface consumed by Tannery-style series-limit routes such as \autoref{ch:concrete-instances-tannery-theorem-namecert}; it does not import a host uniform convergence theorem, a selected infinite sum, quotient stream equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Normal convergence carrier]
\label{def:normal-convergence-carrier}
A $\NormalConvergenceUp$ carrier is a finite $\BHist$ packet
$$
N=(S,A,M,U,R,E,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\RealSeriesUp$ family row. It exposes the inspected real-valued term family and its finite partial-sum windows only through the real-series surface.
\item $A$ is the $\AbsoluteConvergenceUp$ majorant row. It records the absolute majorant family and the finite domination comparison visible to the packet.
\item $M$ is the $\WeierstrassMTestUp$ domination ledger. It displays the finite tail majorant and the exact tail budget used by normal-convergence requests.
\item $U$ is the $\UniformLimitUp$ handoff row. It seals the uniform endpoint read only after the majorant and tail ledger have been displayed.
\item $R$ is the $\RegSeqRatUp$ readback row for the same finite tails, partial sums, and endpoint requests.
\item $E$ is the $\RealUp$ seal reached from the regular readback and uniform handoff, not from a host infinite-sum coordinate.
\item $H$ records componentwise $\hsame$ transport for the series family, absolute-majorant row, M-test ledger, uniform handoff, regular readback, Real seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay of the route
$$
S\longmapsto A\longmapsto M\longmapsto U\longmapsto R\longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\NormalConvergenceUp$, $\RealSeriesUp$, $\AbsoluteConvergenceUp$, $\WeierstrassMTestUp$, $\UniformLimitUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\NormalConvergenceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $S,A,M,U,R,E,H,C,P,L$. It has no coordinate for a host uniform convergence theorem, selected infinite sum, hidden pointwise limit, quotient stream equality, countable-choice selector, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Normal convergence NameCert obligations]
\label{thm:normal-convergence-namecert-obligations}
For every accepted $\NormalConvergenceUp$ carrier
$$
N=(S,A,M,U,R,E,H,C,P,L),
$$
the local $\NameCert_{\NormalConvergenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the real-series family row, absolute-majorant row, M-test domination ledger, uniform-limit handoff, regular readback, Real seal, transport, replay, provenance, and local naming rows;
\item absolute-majorant exactness, requiring $A$ to display the majorant comparison used by every inspected term family read from $S$;
\item uniform-tail exactness, requiring $M$ to store the finite tail budget that the $\WeierstrassMTestUp$ route exports to the uniform handoff;
\item $\RegSeqRatUp$ handoff, requiring $R$ to read the same displayed tail and partial-sum data before any endpoint seal is exported;
\item $\RealUp$ seal non-escape, requiring $E$ to remain downstream of $S,A,M,U,R$ and to export no host uniform convergence theorem, selected infinite sum, hidden pointwise limit, quotient stream equality, countable choice, trichotomy, or ambient $\RealUp$ completeness;
\item componentwise transport, displayed replay, provenance, and local naming for exactly the rows recorded in $H,C,P,L$.
\end{enumerate}
No normal-convergence NameCert obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Project the accepted packet $N=(S,A,M,U,R,E,H,C,P,L)$. The carrier exposes exactly the real-series family, absolute majorant, M-test domination ledger, uniform handoff, regular readback, Real seal, and structural rows.

The majorant side is fixed before any endpoint read. The row $S$ supplies the term-family and partial-sum surface, while $A$ records the absolute-majorant comparison visible for the inspected family.

The finite tail budget is then forced through $M$. Since $M$ is the displayed $\WeierstrassMTestUp$ ledger, every uniform-tail request receives the same majorant exactness row before it can reach $U$.

The rows $U,R,E$ form the endpoint stage. The uniform handoff exposes only the displayed tail route, the regular rational row reads that same route, and the Real seal is downstream of both.

Finally $H,C,P,L$ transport, replay, source, and name the same packet. Because the carrier contains no excluded coordinate for a host uniform convergence theorem, selected infinite sums, hidden pointwise limits, quotient stream equality, choice, trichotomy, or ambient real completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Normal convergence uniform series handoff]
\label{thm:normal-convergence-uniform-series-handoff}
Every endpoint-facing read of an accepted $\NormalConvergenceUp$ packet factors through the displayed route
$$
S\longmapsto A\longmapsto M\longmapsto U\longmapsto R\longmapsto E\longmapsto H,C,P,L .
$$
Thus the read reaches a $\RealUp$ endpoint only after the real-series family row, absolute-majorant row, M-test tail ledger, uniform handoff, and regular rational readback have all been displayed. It does not read a host uniform convergence theorem, selected infinite sum, hidden pointwise limit, quotient stream equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}

\begin{proof}
Begin with an endpoint-facing series request. By \autoref{def:normal-convergence-carrier}, the request first projects the family row $S$ and then the absolute-majorant row $A$.

The normal-convergence control is mediated by $M$. This row is the finite M-test domination ledger, so it provides the exact tail budget that the route may hand to $U$.

The handoff to $U$ and $R$ preserves the same displayed data. The uniform-limit row seals only the endpoint-facing uniform request, and the regular rational row reads the same tail and partial-sum route before a Real seal can appear.

The terminal stage is $E,H,C,P,L$. The Real seal is reached downstream of the displayed route, while transport, replay, provenance, and local naming preserve that same route. Therefore every endpoint-facing read factors through $S,A,M,U,R,E,H,C,P,L$ and cannot bypass the finite normal-convergence certificate surface.
\end{proof}

\closureat{NormalConvergenceUp}{seedStr}

\begin{closurestatus}{\NormalConvergenceUp}
  \constructivestory{A $\NormalConvergenceUp$ packet is generated from a RealSeriesUp family row, an AbsoluteConvergenceUp majorant row, a WeierstrassMTestUp domination ledger, a UniformLimitUp handoff row, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:normal-convergence-carrier}, \autoref{thm:normal-convergence-namecert-obligations}, and \autoref{thm:normal-convergence-uniform-series-handoff} seed the finite normal-convergence certificate surface between real-series families, absolute majorants, M-test tail ledgers, uniform handoffs, regular rational readback, and RealUp endpoint seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host uniform convergence theorems, selected infinite sums, hidden pointwise limits, quotient stream equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, absolute-majorant exactness, uniform-tail exactness, RegSeqRat handoff, Real seal non-escape, transport, replay, provenance, and local naming for BEDC.Derived.NormalConvergenceUp.}
\end{closurestatus}
