\chapter{A Concrete Naming Certificate for $\RegularCauchyCommonTailFilterUp$}
\label{ch:concrete-instances-regular-cauchy-common-tail-filter-namecert}
\origin{human}

Following Bishop and Bridges and Bourbaki, the $\RegularCauchyCommonTailFilterUp$ packet records the finite common-tail filter basis used when several regular Cauchy real names must answer one late-window request before any $\RealUp$ seal is read. It sits after the regular rational source rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the Cauchy-filter route of \autoref{ch:concrete-instances-cauchyfilter-namecert}. The packet is a human-origin L10 basis for shared tail windows; it is not a quotient of Cauchy names, a selected limit, a countable-choice schedule, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy common-tail filter carrier]
\label{def:regular-cauchy-common-tail-filter-carrier}
A $\RegularCauchyCommonTailFilterUp$ carrier is a finite $\BHist$ packet
$$
F=(X,\Sigma,T,R,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the finite family of regular Cauchy source-name rows. Each source is read only through its displayed $\RegSeqRatUp$ surface.
\item $\Sigma$ is the shared $\StreamNameUp$ schedule. It records the finite observation windows, requested tail cut, inspected indices, and synchronization route used for every source in $X$.
\item $T$ is the common-tail basis row. It records the finite upper tail cut, the cofinal refinement requests, and the membership witnesses saying that all later windows are read through the same basis packet.
\item $R$ is the $\RegSeqRatUp$ readback row for the displayed sources at the shared windows of $\Sigma$ and the tail basis $T$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It records the requested radius, tail slack, comparison budget, and exhaustion data consumed by the common-tail test.
\item $Q$ is the $\CauchyFilterUp$ evidence row. It reads the tail basis $T$ as a finite filter-basis route and exports only the displayed cofinal and stability data.
\item $E$ is the terminal $\RealUp$ seal row for the family, available only after $X,\Sigma,T,R,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source family, stream schedule, common-tail basis, readback row, dyadic ledger, Cauchy-filter row, real seal, replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay of the route
$$
X,\Sigma,T,D \longmapsto R \longmapsto Q \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyCommonTailFilterUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\CauchyFilterUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyCommonTailFilterUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these eleven rows. Its classifier compares accepted packets only through $X,\Sigma,T,R,D,Q,E,H,C,P,N$ and has no coordinate for quotient Cauchy equality, selected limits, countable choice, host filter completion, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy common-tail filter NameCert obligations]
\label{thm:regular-cauchy-common-tail-filter-namecert-obligations}
For every accepted $\RegularCauchyCommonTailFilterUp$ carrier
$$
F=(X,\Sigma,T,R,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyCommonTailFilterUp}$ surface consists exactly of the following five finite obligation rows:
\begin{enumerate}
\item carrier admission for the regular Cauchy source family, shared stream schedule, common-tail basis, regular rational readback, dyadic tolerance ledger, Cauchy-filter evidence row, terminal real seal, transport, replay, provenance, and local naming row;
\item common-tail basis discipline, requiring $T$ to display the finite late cut, cofinal refinement requests, and membership witnesses consumed by every source in $X$ through the same $\Sigma$ schedule;
\item tolerance and readback exactness, requiring $R$ and $D$ to expose only the regular rational observations and dyadic budgets read from the displayed source family, shared windows, and common-tail basis;
\item filter and real-seal non-escape, requiring $Q$ and $E$ to remain downstream of $X,\Sigma,T,R,D$ and to export no quotient Cauchy equality, selected limit, countable-choice schedule, host filter completion, or ambient $\RealUp$ completeness;
\item transport, replay, provenance, and naming stability, requiring $H,C,P,N$ to preserve and source exactly the displayed route componentwise.
\end{enumerate}
No common-tail filter-basis obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Project the accepted packet $F=(X,\Sigma,T,R,D,Q,E,H,C,P,N)$. The carrier exposes exactly the regular Cauchy source family, shared schedule, common-tail basis, readback, tolerance, Cauchy-filter, real-seal, and structural rows.

The common-tail data are finite. The schedule $\Sigma$ fixes the inspected windows, while $T$ fixes the late cut and cofinal refinement requests through which every source in $X$ must be read.

The readback and tolerance rows are tied to that same basis. The row $R$ supplies only the regular rational observations visible at the displayed windows, and $D$ supplies only the dyadic radius, slack, comparison budget, and exhaustion data attached to those windows.

The filter and real-seal rows remain downstream. The row $Q$ reads $T$ as a finite Cauchy-filter basis, and $E$ is available only after the source, schedule, tail, readback, tolerance, and filter rows have all been displayed.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since the carrier has no coordinate for quotient Cauchy equality, selected limits, countable choice, host filter completion, ambient real completeness, Lean verification, or a bridge, the five listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Regular Cauchy common-tail filter real-seal boundary]
\label{thm:regular-cauchy-common-tail-filter-real-seal-boundary}
Every $\RealUp$ or completion-facing consumer of an accepted $\RegularCauchyCommonTailFilterUp$ carrier reads the terminal seal only through the finite route
$$
X,\Sigma,T,D \longmapsto R \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus the consumer receives a displayed regular Cauchy source family, one shared StreamName schedule, a common-tail basis, RegSeqRat readback, DyadicRatCore tolerance accounting, CauchyFilter evidence, the terminal RealUp seal, componentwise transport, continuation replay, package provenance, and local naming. It receives no quotient Cauchy equality, selected limit, countable-choice schedule, host filter completion, or ambient $\RealUp$ completeness.
\end{theorem}

\begin{proof}
Begin with an accepted consumer read. The source family is $X$, and the only admissible finite observation route is the shared schedule $\Sigma$ together with the common-tail basis $T$.

The regular rational readback is $R$. It is read from $X$ through the same $\Sigma$ and $T$ rows, so the consumer cannot introduce a second tail schedule or a detached representative family.

The dyadic ledger $D$ supplies the precision budget for the shared tail request. The Cauchy-filter evidence $Q$ then reads that budget and tail basis as a finite filter-basis route.

Only after this route is displayed can $E$ expose the $\RealUp$ seal. The structural rows $H,C,P,N$ preserve the same displayed coordinates under transport, replay, provenance, and local naming.

Because no excluded coordinate occurs in the carrier, the real-seal consumer cannot read quotient Cauchy equality, selected limits, countable choice, host filter completion, or ambient real completeness from the packet.
\end{proof}

\closureat{RegularCauchyCommonTailFilterUp}{seedStr}

\begin{closurestatus}{\RegularCauchyCommonTailFilterUp}
  \constructivestory{A $\RegularCauchyCommonTailFilterUp$ packet is generated from a regular Cauchy source family, a shared StreamName schedule, a common-tail basis row, RegSeqRat readback, a DyadicRatCore tolerance ledger, CauchyFilter evidence, a RealUp terminal seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-common-tail-filter-carrier}, \autoref{thm:regular-cauchy-common-tail-filter-namecert-obligations}, and \autoref{thm:regular-cauchy-common-tail-filter-real-seal-boundary} seed the finite common-tail filter-basis route over shared StreamName windows, RegSeqRat readback, DyadicRatCore tolerances, CauchyFilter evidence, RealUp seals, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient Cauchy equality, selected limits, countable choice, host filter completion, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, common-tail basis discipline, tolerance and readback exactness, filter and Real seal non-escape, transport stability, replay confinement, provenance, and local naming for BEDC.Derived.RegularCauchyCommonTailFilterUp.}
\end{closurestatus}
