\chapter{A Concrete Naming Certificate for $\DedekindCutCompletionUp$}
\label{ch:concrete-instances-dedekind-cut-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DedekindCutCompletionUp$ packet names the finite comparison surface where located Dedekind-cut evidence may be admitted beside regular Cauchy real names without turning $\RealUp$ into a completed Dedekind quotient. It is positioned after the cut-to-Cauchy boundary of \autoref{ch:concrete-instances-dedekind-cut-cauchy-boundary-namecert}, the regular Cauchy completion route of \autoref{ch:concrete-instances-bishop-regular-cauchy-completion-namecert}, the dyadic comparison spine of \autoref{ch:concrete-instances-dyadic-archimedean-namecert}, the regular rational sequence row of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter records how cut-shaped data enters BEDC as finite rows and is compared only through regularization windows, preserving the refusal to treat $\RealUp$ completeness as already proved.

\begin{definition}[Dedekind cut completion carrier]
\label{def:dedekind-cut-completion-carrier}
A $\DedekindCutCompletionUp$ carrier is a finite $\BHist$ packet
$$
D=(L,U,G,W,S,R,A,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the located lower-cut row. It records finite lower observations together with their downward-use discipline.
\item $U$ is the located upper-cut row. It records finite upper observations together with their upward-use discipline.
\item $G$ is the dyadic bracket-witness row. It records the displayed dyadic gaps separating admitted lower and upper observations.
\item $W$ is the finite regularization-window row. It records the bounded window in which cut evidence is translated into regular Cauchy observations.
\item $S$ is the $\StreamNameUp$ observation row opened by the regularization window.
\item $R$ is the $\RegSeqRatUp$ regular Cauchy approximant row read from $S$ under the bracket witnesses in $G$.
\item $A$ is the $\DyadicArchimedeanUp$ comparison row. It stores the finite Archimedean dyadic scale used to compare bracket witnesses with regular Cauchy tolerances.
\item $E$ is the terminal $\RealUp$ seal. It is visible only after $L,U,G,W,S,R,A$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the cut rows, bracket witnesses, regularization windows, stream observations, regular approximants, dyadic comparison row, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located cut request through $L,U,G,W,S,R,A,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DedekindCutCompletionUp$, $\DedekindCutCauchyBoundaryUp$, $\BishopRegularCauchyCompletionUp$, $\DyadicArchimedeanUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindCutCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through finite regularization windows $W$ and the rows displayed downstream of those windows. The carrier has no coordinate for quotient real equality, arbitrary suprema, countable choice, trichotomy, host completeness, or a completeness theorem for $\RealUp$.
\end{definition}

\begin{theorem}[Located cut regularization]
\label{thm:dedekind-cut-completion-located-regularization}
For every accepted $\DedekindCutCompletionUp$ carrier $D=(L,U,G,W,S,R,A,E,H,C,P,N)$, each located cut-side request admitted by $L,U,G$ has a displayed finite regularization route
$$
L,U,G \longrightarrow W \longrightarrow S,R,A \longrightarrow E .
$$
The route reads lower and upper cut rows only through the bracket witnesses in $G$, chooses a bounded regularization window $W$, exposes stream-window observations in $S$, reads regular Cauchy approximants in $R$, compares tolerances through the dyadic Archimedean row $A$, and reaches the terminal $\RealUp$ seal $E$ only after those rows are displayed.
\end{theorem}
\begin{proof}
Carrier projection gives the cut-side rows $L,U,G$ and the regular Cauchy rows $W,S,R,A,E$. The lower and upper observations are not ambient cuts; they are finite rows whose only displayed meeting point is the dyadic bracket-witness row $G$.

The finite window row $W$ is therefore the first comparison surface. It bounds the portion of the cut evidence that a consumer may regularize, so the route never needs a global supremum or a selected cut value.

Inside $W$, the stream row $S$ supplies the inspected observations, the regular sequence row $R$ supplies the regular Cauchy approximants, and the dyadic Archimedean row $A$ supplies the tolerance comparison scale. Only after these rows are visible can the route read the terminal $\RealUp$ seal $E$.
\end{proof}

\begin{theorem}[Dedekind cut completion NameCert obligations]
\label{thm:dedekind-cut-completion-namecert-obligations}
For every accepted $\DedekindCutCompletionUp$ carrier $D=(L,U,G,W,S,R,A,E,H,C,P,N)$, the local $\NameCert_{\DedekindCutCompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located lower row, located upper row, dyadic bracket witnesses, regularization windows, stream observations, regular Cauchy approximants, dyadic Archimedean comparison row, Real seal, transport, replay, provenance, and local naming row;
\item located cut discipline, requiring every lower-row and upper-row read to meet only through the displayed bracket witnesses in $G$;
\item finite regularization, requiring every comparison-facing cut request to choose a displayed window $W$ before reading $S,R,A$;
\item regular Cauchy handoff, requiring stream-window observations, regular approximants, and dyadic tolerance comparisons to be displayed before the $\RealUp$ seal $E$ is visible;
\item classifier stability, requiring componentwise $\hsame$ transport in $H$ and displayed $\Cont$ replay in $C$ to preserve the route $L,U,G,W,S,R,A,E$;
\item ledger exhaustion, requiring $P$ and $N$ to name exactly the displayed packet and no quotient real equality, arbitrary supremum, countable-choice schedule, trichotomy principle, host-completeness theorem, or proof that $\RealUp$ is complete.
\end{enumerate}
No $\DedekindCutCompletionUp$ NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dedekind-cut-completion-carrier}. The finite packet exposes the lower row, upper row, bracket witnesses, regularization windows, stream observations, regular approximants, dyadic comparison data, Real seal, and structural rows $H,C,P,N$.

Located cut discipline follows from the absence of an ambient cut coordinate. Lower and upper observations can be compared only where $G$ supplies a displayed bracket witness.

Finite regularization is forced by the row order. A comparison-facing request must choose $W$ before it can open stream observations, regular Cauchy approximants, or dyadic tolerance comparisons.

The regular Cauchy handoff then reads $S,R,A$ before $E$. Componentwise $\hsame$ transport in $H$ preserves each displayed row, and $\Cont$ replay in $C$ repeats the same route for each accepted request.

Finally, provenance and local naming are exhausted by $P$ and $N$. Since none of the excluded surfaces is a coordinate of $D$, the local certificate cannot export such a surface as a hidden obligation.
\end{proof}

\begin{theorem}[Dedekind cut and Cauchy comparison]
\label{thm:dedekind-cut-completion-cauchy-comparison}
Let $D=(L,U,G,W,S,R,A,E,H,C,P,N)$ and $D'=(L',U',G',W',S',R',A',E',H',C',P',N')$ be accepted $\DedekindCutCompletionUp$ carriers. Any classifier comparison between $D$ and $D'$ is determined by displayed finite regularization windows and their downstream regular Cauchy rows:
$$
W,S,R,A,H,C,P,N
\quad\text{and}\quad
W',S',R',A',H',C',P',N' .
$$
The comparison may transport located cut evidence from $L,U,G$ and $L',U',G'$ into those windows, but it cannot compare packets by quotient real equality, arbitrary suprema, countable choice, trichotomy, host completeness, or the assertion that $\RealUp$ is complete.
\end{theorem}
\begin{proof}
Start with an accepted classifier comparison. By \autoref{def:dedekind-cut-completion-carrier}, the only comparison-facing rows are the displayed regularization windows, stream observations, regular approximants, dyadic comparison rows, and structural transport, replay, provenance, and naming rows.

The cut evidence contributes only through $L,U,G$ and $L',U',G'$. The bracket witnesses in $G$ and $G'$ determine what finite cut-side information enters $W$ and $W'$, but they do not create quotient real equality or a host supremum.

Once the windows are fixed, the comparison is regular Cauchy in form: it reads $S,R,A$ and $S',R',A'$ under the componentwise transport and replay rows. The terminal seals $E$ and $E'$ are reached only after those rows are displayed.

The excluded principles have no coordinates in either carrier. Therefore the classifier compares only through the finite regularization windows and their downstream rows.
\end{proof}

\begin{closurestatus}{\DedekindCutCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-cut-completion-carrier}, \autoref{thm:dedekind-cut-completion-located-regularization}, \autoref{thm:dedekind-cut-completion-namecert-obligations}, and \autoref{thm:dedekind-cut-completion-cauchy-comparison} seed the finite comparison packet admitting located Dedekind-cut evidence through regular Cauchy windows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient real equality, arbitrary suprema, countable choice, trichotomy, host completeness, Lean verification, bridge checking, or that $\RealUp$ is complete.}
  \upgradepath{Lean verification requires a theorem for carrier admission, located cut discipline, finite regularization, regular Cauchy handoff, classifier stability, and ledger exhaustion for BEDC.Derived.DedekindCutCompletionUp.}
  \constructivestory{A $\DedekindCutCompletionUp$ packet is generated from located lower and upper cut rows, dyadic bracket witnesses, finite regularization windows, StreamName observations, RegSeqRat approximants, a DyadicArchimedean comparison row, a terminal Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
