\chapter{A Concrete Naming Certificate for $\UniformConvergenceSeriesUp$}
\label{ch:concrete-instances-uniform-convergence-series-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\UniformConvergenceSeriesUp$ packet records the finite handoff from uniform Cauchy control of real-series partial sums to a uniform-limit surface. It sits over the real-series packet of \autoref{ch:concrete-instances-realseries-namecert}, the uniform Cauchy series packet of \autoref{ch:concrete-instances-uniform-cauchy-series-namecert}, the uniform-limit endpoint packet of \autoref{ch:concrete-instances-uniformlimit-namecert}, the majorant-test route of \autoref{ch:concrete-instances-weierstrassmtest-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives later power-series, real-function, and continuity-transfer chapters a named theorem-level boundary without treating $\UniformCauchySeriesUp$ itself as an infinite-sum object.

\begin{definition}[Uniform convergence series carrier]
\label{def:uniform-convergence-series-carrier}
A $\UniformConvergenceSeriesUp$ carrier is a finite $\BHist$ packet
$$
U=(A,S,W,D,Q,L,M,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the real-valued term-family row. Each summand is read only through displayed finite windows before it is admitted to a partial-sum comparison.
\item $S$ is the $\RealSeriesUp$ partial-sum row. It records finite series windows, displayed partial sums, and the shared real-series tail threshold.
\item $W$ is the $\StreamNameUp$ schedule row used by the partial sums and by the uniform tail request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It records the requested radius, dyadic slack, finite addition budget, and exhausted comparison windows.
\item $Q$ is the $\RegSeqRatUp$ readback row for the displayed partial sums.
\item $L$ is the $\UniformCauchySeriesUp$ ledger. It records the single uniform tail threshold that works across the displayed parameter window.
\item $M$ is the optional $\WeierstrassMTestUp$ majorant route. When present, it supplies the finite domination and majorant-tail rows used to populate $L$; when absent, $L$ is supplied directly by the uniform Cauchy series packet.
\item $E$ is the $\UniformLimitUp$ endpoint row. It becomes visible only after $S,W,D,Q,L$ and the applicable majorant route $M$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the term-family, real-series, stream-window, dyadic, regular-rational, uniform-Cauchy, majorant, uniform-limit, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
A,S,W,D,Q \longmapsto L \longmapsto M \longmapsto E .
$$
If the majorant route is not used, the $M$ coordinate is the displayed empty majorant branch rather than a hidden summability principle.
\item $P$ is the $\Pkg$ provenance over $\UniformConvergenceSeriesUp$, $\RealSeriesUp$, $\UniformCauchySeriesUp$, $\UniformLimitUp$, $\WeierstrassMTestUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformConvergenceSeriesUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these twelve rows. Its classifier compares accepted packets only through $A,S,W,D,Q,L,M,E,H,C,P,N$ and has no coordinate for host infinite sums, selected limits, quotient equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Uniform convergence series NameCert obligations]
\label{thm:uniform-convergence-series-namecert-obligations}
For every accepted $\UniformConvergenceSeriesUp$ carrier
$$
U=(A,S,W,D,Q,L,M,E,H,C,P,N),
$$
the local $\NameCert_{\UniformConvergenceSeriesUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the term-family row, real-series partial-sum row, stream schedule, dyadic tolerance ledger, regular-rational readback, uniform Cauchy ledger, optional majorant route, uniform-limit endpoint, transport, replay, provenance, and local naming row;
\item partial-sum coverage, requiring every convergence request to read the displayed $\RealSeriesUp$ partial-sum row $S$ before reaching any limit endpoint;
\item uniform-tail exactness, requiring the single threshold row $L$ to answer all displayed parameter-window requests through the same dyadic tolerance ledger $D$ and schedule row $W$;
\item regular readback discipline, requiring $Q$ to be the only regular-rational route by which the finite partial sums are handed to the uniform-limit endpoint;
\item majorant confinement, requiring $M$ to be either the displayed $\WeierstrassMTestUp$ domination route or the displayed empty majorant branch, never a host summability assertion;
\item endpoint factorization, requiring $E$ to remain downstream of $S,W,D,Q,L$ and the applicable $M$ branch;
\item transport, replay, provenance, and naming stability, requiring $H,C,P,N$ to preserve and source exactly the displayed rows componentwise;
\item non-escape, excluding host infinite sums, selected limits, quotient equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
No uniform-convergence-series obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Project the accepted packet $U=(A,S,W,D,Q,L,M,E,H,C,P,N)$. The carrier exposes exactly the term-family row, the real-series partial-sum row, the shared stream schedule, the dyadic ledger, the regular readback, the uniform Cauchy ledger, the optional majorant route, the uniform-limit endpoint, and the structural rows.

The convergence request first consumes the real-series partial sums. The row $S$ supplies the finite partial-sum windows, while $W$ fixes the displayed schedule and $D$ fixes the dyadic tolerance budget used by the comparison.

Uniformity is supplied by $L$. The same threshold row must answer every displayed parameter-window request, so a consumer cannot replace the packet by pointwise convergence data or by a separately chosen limit at each parameter.

The regular readback and majorant branch are then confined. The row $Q$ is the only route into the regular-rational handoff, and $M$ either records the finite Weierstrass majorant route or records that no majorant branch is used.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name that same finite route. Since host infinite sums, selected limits, quotient equality, countable choice, open-cover compactness, and ambient real completeness have no carrier coordinate or replay edge, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Uniform convergence series RealSeries handoff]
\label{thm:uniform-convergence-series-realseries-handoff}
Every $\UniformLimitUp$ endpoint read of an accepted $\UniformConvergenceSeriesUp$ carrier factors through the finite route
$$
A,S,W,D,Q \longmapsto L \longmapsto M \longmapsto E \longmapsto H,C,P,N .
$$
Thus the consumer receives a displayed real-valued term family, $\RealSeriesUp$ partial-sum windows, $\StreamNameUp$ schedules, $\DyadicRatCoreUp$ tolerance accounting, $\RegSeqRatUp$ readback, one $\UniformCauchySeriesUp$ tail ledger, the applicable $\WeierstrassMTestUp$ branch, the $\UniformLimitUp$ endpoint row, componentwise transport, continuation replay, package provenance, and local naming. It receives no host infinite sum, selected limit, quotient equality, countable-choice schedule, open-cover compactness principle, or ambient $\RealUp$ completeness theorem.
\end{theorem}

\begin{proof}
Start with an accepted endpoint read. The term-family row $A$ is visible only through the real-series partial-sum row $S$, and those partial sums are inspected along the schedule row $W$ with the tolerance accounting recorded in $D$.

The regular-rational readback is then forced through $Q$. It is the unique displayed handoff from the finite partial sums to the uniform Cauchy comparison surface, so no quotient equality of series or selected infinite sum is introduced.

The uniform Cauchy step is the row $L$. It supplies the common tail threshold that works for every displayed parameter-window request; if a majorant proof is used, the row $M$ records exactly the Weierstrass domination and majorant-tail rows that populate $L$.

Only after this route is displayed can $E$ expose the $\UniformLimitUp$ endpoint. The structural rows $H,C,P,N$ preserve the same route under componentwise transport, continuation replay, provenance, and local naming.

Induction over the displayed route order proves the factorization. The base stage reads $A,S,W,D,Q$, the uniform-tail stage reads $L$, the majorant branch reads $M$, and the terminal stage reads $E,H,C,P,N$. There is no coordinate outside this route from which a consumer could extract a host infinite sum, selected limit, quotient equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{proof}

\closureat{UniformConvergenceSeriesUp}{seedStr}

\begin{closurestatus}{\UniformConvergenceSeriesUp}
  \constructivestory{A $\UniformConvergenceSeriesUp$ packet is generated from a real-valued term-family row, RealSeries partial-sum windows, StreamName schedules, a DyadicRatCore tolerance ledger, RegSeqRat readback, one UniformCauchySeries tail ledger, an optional WeierstrassMTest majorant route, a UniformLimit endpoint row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-convergence-series-carrier}, \autoref{thm:uniform-convergence-series-namecert-obligations}, and \autoref{thm:uniform-convergence-series-realseries-handoff} seed the finite theorem-level route from RealSeries partial sums and UniformCauchySeries tail control to the UniformLimit endpoint surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, selected limits, quotient equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, partial-sum coverage, uniform-tail exactness, regular readback discipline, majorant confinement, endpoint factorization, transport, replay, provenance, and local naming for BEDC.Derived.UniformConvergenceSeriesUp.}
\end{closurestatus}
