\chapter{A Concrete Naming Certificate for $\RegularCauchyTranslationUp$}
\label{ch:concrete-instances-regular-cauchy-translation-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyTranslationUp$ packet records constant translation of a regular Cauchy real name as displayed finite BEDC data. It sits beside the two-source addition surface of \autoref{ch:concrete-instances-regularcauchysum-namecert}, the sign-flip route of \autoref{ch:concrete-instances-regularcauchynegation-namecert}, the rational scaling route of \autoref{ch:concrete-instances-regularcauchyscale-namecert}, the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source boundary of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives Real and Completion consumers one finite route for reading $x+c$ through the displayed source and constant rows, without importing host real addition, quotient stream equality, selected limits, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy translation carrier]
\label{def:regular-cauchy-translation-carrier}
A $\RegularCauchyTranslationUp$ carrier is a finite $\BHist$ packet
$$
T_c=(X,Q,W_X,W_Q,D_X,D_Q,A,E,R,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source $\RegSeqRatUp$ row for the regular Cauchy real name being translated.
\item $Q$ is the constant row, displayed either as a dyadic endpoint row or as a rational row whose dyadic readings are supplied through $\DyadicRatCoreUp$.
\item $W_X$ and $W_Q$ are synchronized $\StreamNameUp$ windows. The row $W_X$ opens the requested source observation, while $W_Q$ opens the stationary finite window for the constant row at the same precision request.
\item $D_X$ and $D_Q$ are the translated dyadic endpoint rows, recording the source endpoint read from $X$ and the constant endpoint read from $Q$ in the common dyadic ledger.
\item $A$ is the $\RegularCauchySumUp$ handoff row adding the source regular name to the constant regular row generated from $Q$.
\item $E$ is the finite error ledger combining source tolerance, constant display tolerance, dyadic endpoint addition tolerance, and the output tolerance consumed by the sum handoff.
\item $R$ is the $\RegSeqRatUp$ readback row produced by the displayed sum route.
\item $Z$ is the $\RealUp$ seal row reached only after $X,Q,W_X,W_Q,D_X,D_Q,A,E,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, constant, synchronized windows, dyadic endpoint rows, sum handoff, finite ledger, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any translation-facing precision request through $X,Q,W_X,W_Q,D_X,D_Q,A,E,R,H,P,N$ before the seal row $Z$ is exposed.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyTranslationUp$, $\RegularCauchySumUp$, $\RegularCauchyNegationUp$, $\RegularCauchyScaleUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTranslationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Q,W_X,W_Q,D_X,D_Q,A,E,R,Z,H,C,P,N$. The carrier has no coordinate for host real addition, quotient stream equality, a selected representative, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Regular Cauchy translation NameCert obligations]
\label{thm:regular-cauchy-translation-namecert-obligations}
For every accepted $\RegularCauchyTranslationUp$ carrier
$$
T_c=(X,Q,W_X,W_Q,D_X,D_Q,A,E,R,Z,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyTranslationUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item source-and-constant admission, requiring the source $\RegSeqRatUp$ row $X$ and the displayed constant row $Q$ to be present before any translated read is exposed;
\item synchronized-window exposure, requiring $W_X$ and $W_Q$ to open the source and constant observations at the same finite precision request;
\item dyadic endpoint and ledger exactness, requiring $D_X,D_Q,E$ to account for the source endpoint, constant endpoint, endpoint addition, and output tolerance used by the translation;
\item sum-route handoff, requiring the translated readback $R$ to pass through the $\RegularCauchySumUp$ row $A$ and through no host addition operation;
\item structural naming, requiring $Z,H,C,P,N$ to expose the terminal $\RealUp$ seal, componentwise transport, continuation replay, package provenance, and local $\NameCert$ row for exactly this finite translation packet.
\end{enumerate}
No translation obligation is stored outside these five rows, and the surface refuses host real addition, quotient stream equality, selected representatives, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, and bridge checking as local data.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source row $X$, constant row $Q$, synchronized windows $W_X,W_Q$, dyadic endpoint rows $D_X,D_Q$, sum handoff $A$, finite ledger $E$, readback row $R$, seal row $Z$, and structural rows $H,C,P,N$ are the whole visible packet.

Read the source and constant windows first. The row $W_X$ supplies the finite observation of the source regular name, while $W_Q$ supplies the stationary constant observation at the same precision request. Thus the source endpoint and constant endpoint are compared only after both windows are displayed.

Next read the dyadic and budget rows. The rows $D_X$ and $D_Q$ supply the endpoint data consumed by the $\RegularCauchySumUp$ handoff, and $E$ records the source tolerance, constant tolerance, endpoint-addition tolerance, and output tolerance before $R$ is available.

Finally replay the route through the structural rows. Since $A$ is the only addition handoff and every seal-facing read must pass through $R$ before $Z$, no quotient stream, selected representative, host addition operation, countable-choice selector, trichotomy witness, ambient completeness theorem, Lean verification, or bridge credential can be read from the local packet.
\end{proof}

\begin{theorem}[Regular Cauchy translation real seal handoff]
\label{thm:regular-cauchy-translation-real-seal-handoff}
Every $\RealUp$-facing read exported by an accepted $\RegularCauchyTranslationUp$ carrier factors through the displayed constant row and sum route
$$
(X,Q)\longmapsto (W_X,W_Q)\longmapsto (D_X,D_Q)\longmapsto A\longmapsto E\longmapsto R\longmapsto Z .
$$
Thus the consumer sees the source regular row, the constant dyadic or rational row, synchronized StreamName windows, translated dyadic endpoint rows, the $\RegularCauchySumUp$ handoff, the finite error ledger, the $\RegSeqRatUp$ readback, and the terminal $\RealUp$ seal. It receives no host real addition, quotient stream equality, selected representative, countable-choice witness, trichotomy decision, ambient completeness coordinate, Lean verification, or bridge checking.
\end{theorem}
\begin{proof}
Begin with a Real-facing read of the accepted packet. The carrier exposes the seal row $Z$ only downstream of the readback row $R$, so the read must first pass through the regular readback route.

The readback route is fixed by the constant row and the sum handoff. The source row $X$ and constant row $Q$ are opened through synchronized windows $W_X,W_Q$, their dyadic endpoint rows are read as $D_X,D_Q$, and the displayed $\RegularCauchySumUp$ row $A$ is then the only route forming the translated regular name.

The finite ledger precedes the seal. The row $E$ accounts for source, constant, endpoint-addition, and output tolerances before $R$ and then $Z$ can be consumed.

The structural rows preserve this factorization. Componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local naming do not add another Real-facing coordinate, so every accepted seal read factors through the displayed constant row and sum route and cannot escape to the refused principles.
\end{proof}

\closureat{RegularCauchyTranslationUp}{seedStr}

\begin{closurestatus}{\RegularCauchyTranslationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-translation-carrier}, \autoref{thm:regular-cauchy-translation-namecert-obligations}, and \autoref{thm:regular-cauchy-translation-real-seal-handoff} seed the finite constant-translation surface over one $\RegSeqRatUp$ source row, a displayed dyadic or rational constant row, synchronized $\StreamNameUp$ windows, $\DyadicRatCoreUp$ endpoint rows, a $\RegularCauchySumUp$ handoff, finite error ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real addition, quotient stream equality, selected representatives, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked source-and-constant admission, synchronized-window exposure, dyadic endpoint and ledger exactness, sum-route handoff, Real seal non-escape, componentwise transport, continuation replay, provenance, and local naming for BEDC.Derived.RegularCauchyTranslationUp.}
  \constructivestory{A $\RegularCauchyTranslationUp$ packet is generated from a RegSeqRat source row, a displayed dyadic or rational constant row, synchronized StreamName windows, translated DyadicRatCore endpoint rows, a RegularCauchySum handoff, a finite error ledger, RegSeqRat readback, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
