\chapter{A Concrete Naming Certificate for $\YonedaCompletionUp$}
\label{ch:concrete-instances-yoneda-completion-namecert}
\origin{human}

Following Lawvere's enriched metric spaces and the Isbell--Yoneda completion tradition, the $\YonedaCompletionUp$ packet records a presheaf-style completion route as finite BEDC NameCert data. It sits over the formal-ball surfaces of \autoref{ch:concrete-instances-formalball-namecert} and \autoref{ch:concrete-instances-formal-ball-completion-namecert}, the metric source of \autoref{ch:concrete-instances-metric-namecert}, the Cauchy-net route of \autoref{ch:concrete-instances-cauchynet-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic radius ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives completion consumers a finite Yoneda-style handoff without quotient completion, selected limits, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Yoneda completion carrier]
\label{def:yoneda-completion-carrier}
A $\YonedaCompletionUp$ carrier is a finite $\BHist$ packet
$$
Y=(M,B,F,D,S,Q,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricUp$ source row, including the point classifier, displayed distance observations, and finite comparison histories read by completion consumers.
\item $B$ is the $\FormalBallUp$ radius-tagged observation row over $M$.
\item $F$ is the $\FormalBallCompletionUp$ row, exposing the rounded formal-ball completion route available before any Yoneda-facing read is exported.
\item $D$ is the $\DyadicRatCoreUp$ radius ledger, recording positive-radius witnesses, dyadic refinements, strict comparisons, and radius-sum budgets used by $B$ and $F$.
\item $S$ is the $\StreamNameUp$ finite-window schedule for center observations, radius requests, and presheaf-profile probes.
\item $Q$ is the $\CauchyNetUp$ comparison row. It records the directed-window route through which a finite Yoneda profile can hand off to ordinary Cauchy data.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the retained stream windows and dyadic budgets.
\item $A$ is the $\RealUp$ seal, reachable only through the displayed $D,S,R$ route and not as an ambient completeness principle.
\item $H$ records componentwise $\hsame$ transport for metric sources, formal balls, formal-ball completion rows, dyadic ledgers, stream windows, Cauchy-net comparisons, regular readbacks, real seals, replay data, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
M,B,F,D,S \longmapsto Q,R \longmapsto A .
$$
\item $P$ is the $\Pkg$ provenance over $\YonedaCompletionUp$, $\MetricUp$, $\FormalBallUp$, $\FormalBallCompletionUp$, $\CauchyNetUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\YonedaCompletionUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these twelve rows. Its classifier compares accepted packets only through $M,B,F,D,S,Q,R,A,H,C,P,N$ and has no coordinate for quotient completion, selected limit representatives, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Yoneda completion NameCert obligations]
\label{thm:yoneda-completion-namecert-obligations}
For an accepted $\YonedaCompletionUp$ carrier
$$
Y=(M,B,F,D,S,Q,R,A,H,C,P,N),
$$
the local $\NameCert_{\YonedaCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the metric source row, formal-ball row, formal-ball completion row, dyadic radius ledger, stream-window schedule, Cauchy-net comparison row, regular rational readback, real seal, transport, replay, provenance, and local naming row;
\item Yoneda-profile exposure, requiring every completion-facing profile to be read as a finite formal-ball family over $M,B,F$ before any Cauchy-net or real-facing handoff is available;
\item radius and window exactness, requiring each formal-ball radius, refinement, and comparison used by the profile to be accounted for in $D$ and inspected through $S$;
\item Cauchy handoff discipline, requiring $Q$ to compare the finite profile with a displayed $\CauchyNetUp$ route rather than replacing it with a quotient of Cauchy names;
\item regular rational and real readback discipline, requiring $R$ and $A$ to be downstream of the same $D,S,Q$ ledger;
\item classifier transport, requiring $H$ and $C$ to preserve the displayed route componentwise and to replay only the listed coordinates;
\item non-escape, excluding quotient completion, selected limits, countable choice, open-cover compactness, and ambient $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:yoneda-completion-carrier}. The accepted packet exposes exactly the metric, formal-ball, formal-ball completion, dyadic, stream-window, Cauchy-net comparison, regular readback, real seal, and structural rows.

Yoneda-profile exposure is forced by the order of the displayed rows. A completion-facing profile first reads $M,B,F$ as finite formal-ball data, so it cannot begin from a quotient completion object or a selected representative.

Radius and window exactness follows from $D$ and $S$. Every radius comparison and every inspected center observation used by the profile has a dyadic budget and a finite stream-window address before the profile can be consumed.

The Cauchy handoff is the row $Q$. It compares the same finite profile with a displayed directed-window route, and therefore supplies no quotient of Cauchy names and no countable-choice selector.

The regular rational and real readbacks are downstream. The rows $R$ and $A$ can be read only after the dyadic, stream-window, and Cauchy-net comparison rows have been displayed.

Finally $H,C,P,N$ transport, replay, source, and name only the listed rows. Since the excluded host principles have no coordinate in the carrier, they cannot appear as local NameCert obligations.
\end{proof}

\begin{theorem}[Yoneda completion formal-ball density]
\label{thm:yoneda-completion-formal-ball-density}
Let
$$
Y=(M,B,F,D,S,Q,R,A,H,C,P,N)
$$
be an accepted $\YonedaCompletionUp$ carrier. Every displayed Yoneda profile exported by $Y$ is densely probed by finite $\FormalBallUp$ data: for each retained profile request there is a formal-ball row in $B$, a formal-ball completion read in $F$, a dyadic radius budget in $D$, and a stream-window address in $S$ whose replay through $C$ reaches the same profile request. Thus density is recorded as finite formal-ball coverage, not as a selected limit and not as an ambient completion theorem.
\end{theorem}
\begin{proof}
Fix a retained profile request. By carrier admission the request is part of the displayed $\YonedaCompletionUp$ packet, so its only profile-facing coordinates are $M,B,F,D,S$ before any downstream readback occurs.

The formal-ball row $B$ supplies the radius-tagged probe over the metric source $M$. The formal-ball completion row $F$ records that the same probe participates in the rounded completion route.

The rows $D$ and $S$ bind the probe to finite data. The radius is accounted for by the dyadic ledger $D$, and the inspected center observation has a stream-window address in $S$.

Replay through $C$ identifies this finite formal-ball coverage with the retained profile request. The real-facing rows $R,A$ and the Cauchy-net comparison row $Q$ are downstream of the same coverage route, so they cannot supply a selected limit or ambient completeness principle.
\end{proof}

\begin{theorem}[Yoneda completion regular Cauchy handoff]
\label{thm:yoneda-completion-regular-cauchy-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ read exported by an accepted $\YonedaCompletionUp$ carrier factors through the finite route
$$
M,B,F,D,S \longmapsto Q \longmapsto R \longmapsto A .
$$
Consequently the packet hands finite Yoneda-profile data to regular Cauchy consumers only through the displayed $\FormalBallUp$, $\FormalBallCompletionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\CauchyNetUp$, and $\RegSeqRatUp$ rows. It does not export quotient completion, selected limits, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier and project its readback rows. A $\RegSeqRatUp$ or $\RealUp$ consumer can reach $R$ or $A$ only by following the replay route named in \autoref{def:yoneda-completion-carrier}.

The first stage of that route is formal-ball data over the metric source. The rows $M,B,F$ expose the metric observations, formal-ball probes, and formal-ball completion reads.

The second stage binds those probes to finite budgets. The dyadic ledger $D$ and stream schedule $S$ record the radius comparisons and inspected windows used by the profile.

The Cauchy comparison row $Q$ then supplies the ordinary directed-window handoff. Since $Q$ is downstream of $M,B,F,D,S$, it cannot replace the finite profile by a quotient Cauchy object or a selected limit.

Finally $R$ and $A$ are read from that same route. Componentwise transport and replay through $H$ and $C$, together with provenance and local naming through $P,N$, preserve the factorization and expose no additional completeness principle.
\end{proof}

\closureat{YonedaCompletionUp}{seedStr}

\begin{closurestatus}{\YonedaCompletionUp}
  \constructivestory{A $\YonedaCompletionUp$ packet is generated from a displayed MetricUp source, FormalBallUp probes, FormalBallCompletionUp rounded reads, DyadicRatCore radius ledgers, StreamName windows, CauchyNet comparisons, RegSeqRat readbacks, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:yoneda-completion-carrier}, \autoref{thm:yoneda-completion-namecert-obligations}, \autoref{thm:yoneda-completion-formal-ball-density}, and \autoref{thm:yoneda-completion-regular-cauchy-handoff} seed the finite Yoneda completion route over formal-ball profiles, directed Cauchy comparison, regular rational readback, real sealing, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected limits, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Yoneda-profile exposure, radius and window exactness, Cauchy handoff discipline, regular rational and real readback discipline, classifier transport, formal-ball density, and non-escape for BEDC.Derived.YonedaCompletionUp.}
\end{closurestatus}
