\chapter{A Concrete Naming Certificate for $\CantorCylinderBasisUp$}
\label{ch:concrete-instances-cantor-cylinder-basis-namecert}
\origin{human}

Following Brouwer's finite-prefix reading of choice sequences and the
Bishop--Bridges cylinder terminology for Cantor space, the
$\CantorCylinderBasisUp$ packet records the basic clopen cylinder surface of
$\CantorSpaceUp$ as finite NameCert data. It sits after the Cantor-space
carrier of \autoref{ch:concrete-instances-cantorspace-namecert}, the unary
finite-window interface of \autoref{ch:concrete-instances-streamname-namecert},
the two-endpoint discipline of \autoref{ch:concrete-instances-bool-namecert},
and the ordered prefix spine of \autoref{ch:concrete-instances-list-namecert}.
The packet names prefix cylinders by displayed finite routes; it is not a
host function extensionality principle, a quotient of infinite streams, a
completed infinite product, a fan-theorem compactness argument, a
countable-choice selector, or an appeal to $\RealUp$ completeness.

\begin{definition}[Cantor cylinder basis carrier]
\label{def:cantor-cylinder-basis-carrier}
A $\CantorCylinderBasisUp$ carrier is a finite $\BHist$ packet
$$
Z=(C,S,W,B,L,R,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $C$ is the source $\CantorSpaceUp$ packet whose public observations are
read only through finite prefix windows;
\item $S$ is the $\StreamNameUp$ schedule row selecting the requested finite
prefix positions;
\item $W$ is the finite cylinder-window row, including the displayed prefix
and the shorter windows used by downstream refinement reads;
\item $B$ is the $\BoolUp$ endpoint ledger assigning visible Boolean rows to
the positions of $W$;
\item $L$ is the $\ListUp$ spine row ordering the prefix entries and recording
their finite length;
\item $R$ is the refinement ledger saying which shorter or longer displayed
prefix rows are being compared inside the same cylinder family;
\item $H$ is the componentwise $\hsame$ transport row for $C,S,W,B,L,R$;
\item $K$ is the displayed $\Cont$ replay row for cylinder reads and prefix
refinements already accepted by the packet;
\item $P$ is the $\Pkg$ provenance over $\CantorCylinderBasisUp$,
$\CantorSpaceUp$, $\StreamNameUp$, $\BoolUp$, $\ListUp$, $\BHist$, $\hsame$,
$\Cont$, and the local naming row;
\item $N$ is the local $\NameCert_{\CantorCylinderBasisUp}$ row.
\end{enumerate}
The carrier has no coordinate for host-level maps $\NatUp \to \BoolUp$,
quotient stream equality, completed infinite products, fan-theorem
compactness, countable choice, or $\RealUp$ completeness.
\end{definition}

\begin{definition}[Cantor cylinder basis classifier]
\label{def:cantor-cylinder-basis-classifier}
Two accepted $\CantorCylinderBasisUp$ carriers
$$
Z=(C,S,W,B,L,R,H,K,P,N)
\quad\hbox{and}\quad
Z'=(C',S',W',B',L',R',H',K',P',N')
$$
are classified as the same basis element exactly when their displayed
$\StreamNameUp$ schedules select the same finite prefix length and their
$\BoolUp$ rows agree componentwise along the ordered $\ListUp$ spine. The
comparison is transported only through $H,H'$ and replayed only through
$K,K'$. It does not compare host functions, quotient streams, infinite tails,
or completed product coordinates.
\end{definition}

\begin{theorem}[Cantor cylinder basis NameCert obligations]
\label{thm:cantor-cylinder-basis-namecert-obligations}
The local $\NameCert_{\CantorCylinderBasisUp}$ surface of
\autoref{def:cantor-cylinder-basis-carrier} consists exactly of the finite
carrier admission, classifier transport, prefix refinement, StreamName--Bool
scope, continuation replay, provenance, and non-escape obligations displayed
by
$$
C,S,W,B,L,R,H,K,P,N .
$$
Every obligation is checked by finite prefix data over the sibling
$\CantorSpaceUp$, $\StreamNameUp$, $\BoolUp$, and $\ListUp$ packets.
\end{theorem}
\begin{proof}
Carrier admission is projection of the ten displayed rows in
\autoref{def:cantor-cylinder-basis-carrier}. The source Cantor packet supplies
the finite observation context, while $S,W,B,L$ expose the requested prefix as
StreamName windows, Boolean endpoints, and a List spine.

Classifier transport uses
\autoref{def:cantor-cylinder-basis-classifier}. Once the finite prefix length
and componentwise Boolean rows are fixed, $H$ transports the same finite
rows and $K$ replays them without adding any host-level stream coordinate.

The remaining obligations are inspection of $R,H,K,P,N$. Prefix refinement is
recorded as a finite relation between displayed prefix rows, continuation
replay is confined to the accepted rows, and provenance keeps the route inside
the listed sibling chapters.

Non-escape follows because no carrier coordinate supplies host function
extensionality, quotient stream equality, completed infinite products,
fan-theorem compactness, countable choice, or $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Cantor cylinder basis prefix refinement]
\label{thm:cantor-cylinder-basis-prefix-refinement}
Let $Z=(C,S,W,B,L,R,H,K,P,N)$ be an accepted
$\CantorCylinderBasisUp$ carrier. If a displayed prefix row in $R$ extends
another displayed prefix row in the same carrier, then the longer cylinder
read factors through the shorter cylinder read together with the additional
finite $\BoolUp$ rows on the suffix. If the rows are incompatible at a visible
position, the classifier rejects the shared basis element at that same finite
position.
\end{theorem}
\begin{proof}
Read the two prefix rows from $R$. The shorter row and the longer row are both
subwindows of the displayed cylinder-window row $W$, so their positions are
already scheduled by the same $\StreamNameUp$ row $S$.

In the extension case, the common part is ordered by the same initial segment
of the $\ListUp$ spine $L$. The suffix is a finite list of additional
$\BoolUp$ rows from $B$, and replay through $K$ appends only those visible
rows to the already accepted shorter read.

In the incompatible case, some displayed position carries different
$\BoolUp$ endpoint rows. The classifier of
\autoref{def:cantor-cylinder-basis-classifier} reads that position directly
through the shared finite spine and rejects equality there, without comparing
infinite tails or host functions.
\end{proof}

\begin{theorem}[Cantor cylinder basis StreamName-Bool scope]
\label{thm:cantor-cylinder-basis-streamname-scope}
Every public read exported by an accepted $\CantorCylinderBasisUp$ carrier
reaches downstream countable-name consumers only through the finite route
$$
\CantorSpaceUp,\ \StreamNameUp,\ \BoolUp,\ \ListUp,\ \NameCert_{\CantorCylinderBasisUp}.
$$
The route exposes prefix-cylinder membership, refinement, and incompatibility
only as displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$
data. It does not export host function extensionality, quotient streams,
completed infinite products, fan-theorem compactness, countable choice, or
$\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a public consumer read of $Z$. The Cantor source $C$ can be read
only through the finite prefix discipline of
\autoref{ch:concrete-instances-cantorspace-namecert}; the requested positions
are then exposed by the $\StreamNameUp$ schedule $S$ and the cylinder window
$W$.

The visible values are exactly the $\BoolUp$ rows in $B$, ordered by the
$\ListUp$ spine $L$. Refinement information is read from $R$, transported by
$H$, and replayed by $K$ before provenance and local naming are recorded in
$P,N$.

Thus every public route remains inside the displayed finite rows. The excluded
objects are not supplied by the carrier, classifier, or refinement ledger, so
no downstream consumer can obtain them from the cylinder-basis packet.
\end{proof}

\begin{closurestatus}{\CantorCylinderBasisUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cantor-cylinder-basis-carrier}, \autoref{def:cantor-cylinder-basis-classifier}, \autoref{thm:cantor-cylinder-basis-namecert-obligations}, \autoref{thm:cantor-cylinder-basis-prefix-refinement}, and \autoref{thm:cantor-cylinder-basis-streamname-scope} seed the finite prefix-cylinder basis surface over CantorSpace, StreamName, Bool, and List rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not close host function extensionality, quotient stream equality, completed infinite products, fan-theorem compactness, countable choice, Real completeness, or a standard bridge.}
  \upgradepath{The next step is obligationClosure: carrier admission, classifier transport, prefix refinement, StreamName-Bool routing, and non-escape must be discharged as local rows.}
  \constructivestory{The construction starts from a finite CantorSpace prefix, reads the selected positions through StreamName windows, records Bool endpoints along a List spine, and exposes only hsame, Cont, Pkg, and local NameCert rows to downstream consumers.}
\end{closurestatus}
