\chapter{A Concrete Naming Certificate for $\StarRefinementUniformCoverUp$}
\label{ch:concrete-instances-star-refinement-uniform-cover-namecert}
\origin{human}

Following Kelley and Bourbaki on uniform spaces and star refinements of uniform covers, the $\StarRefinementUniformCoverUp$ packet records the finite cover-refinement surface needed by the L10 completion route. It sits after the uniform-space surface of \autoref{ch:concrete-instances-uniformspace-namecert}, the entourage-base surface of \autoref{ch:concrete-instances-entourage-base-namecert}, the filter-base surface of \autoref{ch:concrete-instances-filterbase-namecert}, the rounded-ideal completion surface of \autoref{ch:concrete-instances-rounded-ideal-completion-namecert}, and the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}. The packet names displayed cover and star-refinement rows only; it does not import open-cover compactness, selected refinements, choice, or ambient completeness.

\begin{definition}[StarRefinementUniformCover carrier]
\label{def:star-refinement-uniform-cover-carrier}
A $\StarRefinementUniformCoverUp$ carrier is a finite $\BHist$ packet
$$
S=(U,E,F,R,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the uniform-cover row. It records the finite cover family read from the $\UniformSpaceUp$ entourage interface and the membership windows through which a downstream completion consumer may inspect it.
\item $E$ is the $\EntourageBaseUp$ row. It supplies the entourage-basis refinement data whose square or composite containment witnesses the star-refinement relation.
\item $F$ is the $\FilterBaseUp$ row. It records the directed finite base route that transports cover refinements to Cauchy and completion consumers.
\item $R$ is the $\RoundedIdealCompletionUp$ row. It records the rounded-ideal completion consumer that may request the refinement as a formal-ball neighbourhood boundary.
\item $M$ is the $\MetricCompletionUp$ row. It records the metric-completion consumer that may read the same refinement through metric entourage or ball data.
\item $H$ records componentwise $\hsame$ transport for the uniform cover, entourage base, filter base, rounded-ideal completion, metric completion, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
U,E,F \longmapsto R,M \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\StarRefinementUniformCoverUp$, $\UniformSpaceUp$, $\EntourageBaseUp$, $\FilterBaseUp$, $\RoundedIdealCompletionUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StarRefinementUniformCoverUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these nine rows. Its classifier compares accepted packets only through $U,E,F,R,M,H,C,P,N$ and has no coordinate for open-cover compactness, a choice-selected refinement, a host star operation, or ambient completeness.
\end{definition}

\begin{theorem}[StarRefinementUniformCover NameCert obligations]
\label{thm:star-refinement-uniform-cover-namecert-obligations}
For an accepted $\StarRefinementUniformCoverUp$ carrier
$$
S=(U,E,F,R,M,H,C,P,N),
$$
the local $\NameCert_{\StarRefinementUniformCoverUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the uniform-cover row, entourage-base row, filter-base row, rounded-ideal completion row, metric-completion row, transport, replay, provenance, and local naming row;
\item star-refinement containment, requiring the displayed entourage basis in $E$ to witness that every star of the refined cover lies inside a displayed member of the cover row $U$;
\item filter-base handoff, requiring the directed base row $F$ to preserve the same refinement relation for Cauchy and completion consumers;
\item rounded-ideal completion handoff, requiring $R$ to read the refinement only as a formal-ball neighbourhood boundary already routed through $U,E,F$;
\item metric-completion handoff, requiring $M$ to read the same refinement only through the displayed metric entourage or ball data already routed through $U,E,F$;
\item classifier transport, requiring $\hsame$ comparison to preserve the uniform-cover, entourage-base, filter-base, rounded-ideal, metric-completion, replay, provenance, and local naming rows componentwise;
\item non-escape, excluding open-cover compactness, choice, selected refinements, host star operations, and ambient completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:star-refinement-uniform-cover-carrier}. The accepted packet exposes exactly the uniform-cover, entourage-base, filter-base, rounded-ideal completion, metric-completion, transport, replay, provenance, and local naming rows.

Star-refinement containment is read from $E$ against $U$. The entourage-basis row supplies the finite refinement witness, and the cover row supplies the displayed members into which each star is contained.

The completion handoffs then consume the same route. The filter-base row $F$ carries directed refinement data to Cauchy-style consumers, while $R$ and $M$ read the route as rounded-ideal and metric-completion neighbourhood data.

Finally $H,C,P,N$ preserve the route componentwise. Since the carrier has no row for compactness of arbitrary open covers, selected refinements, choice, a host star operation, or ambient completeness, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[StarRefinementUniformCover completion handoff]
\label{thm:star-refinement-uniform-cover-completion-handoff}
Let
$$
S=(U,E,F,R,M,H,C,P,N)
$$
be an accepted $\StarRefinementUniformCoverUp$ carrier. Every completion-facing consumer of the star-refinement row factors through the finite route
$$
U\longmapsto E\longmapsto F\longmapsto R,M\longmapsto H,C,P,N .
$$
The handoff supplies $\RoundedIdealCompletionUp$ and $\MetricCompletionUp$ with a displayed refinement row for uniform-cover arguments. It does not export open-cover compactness, choice, selected refinements, a host star operation, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the accepted carrier $S$. The uniform-cover row $U$ is the only cover entry point, so every completion-facing read first exposes the finite cover family and its membership windows.

The entourage-base row $E$ then supplies the star-refinement witness. Its containment data refine the cover row already displayed by $U$, and the filter-base row $F$ preserves that relation as a directed finite base route.

The completion consumers are downstream of this route. The rounded-ideal row $R$ reads the refinement as a formal-ball neighbourhood boundary, while the metric-completion row $M$ reads it through displayed metric entourage or ball data.

Transport by $H$, replay by $C$, provenance by $P$, and naming by $N$ preserve the same finite route. No excluded host-side principle is available to any completion consumer.
\end{proof}

\closureat{StarRefinementUniformCoverUp}{seedStr}

\begin{closurestatus}{\StarRefinementUniformCoverUp}
  \constructivestory{A $\StarRefinementUniformCoverUp$ packet is generated from a uniform-cover row, an EntourageBaseUp refinement witness, a FilterBaseUp directed base route, RoundedIdealCompletionUp and MetricCompletionUp consumer rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:star-refinement-uniform-cover-carrier}, \autoref{thm:star-refinement-uniform-cover-namecert-obligations}, and \autoref{thm:star-refinement-uniform-cover-completion-handoff} seed the uniform-cover star-refinement surface for L10 completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, choice, selected refinements, host star operations, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, star-refinement containment, filter-base handoff, rounded-ideal completion handoff, metric-completion handoff, classifier transport, and non-escape for BEDC.Derived.StarRefinementUniformCoverUp.}
\end{closurestatus}
