\chapter{A Concrete Naming Certificate for $\FrechetCompletionUp$}
\label{ch:concrete-instances-frechet-completion-namecert}
\origin{human}

Following Frechet on metric convergence, Bourbaki and Kelley on filters and nets, and Bishop--Bridges on constructive completion, the $\FrechetCompletionUp$ packet records the L10 filter-completion surface as finite BEDC NameCert data. It consumes the completion source of \autoref{ch:concrete-instances-metriccompletion-namecert}, the filter route of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the net route of \autoref{ch:concrete-instances-cauchynet-namecert}, and the separated-limit boundary of \autoref{ch:concrete-instances-separatedcompletion-namecert}. It also reads finite stream windows from \autoref{ch:concrete-instances-streamname-namecert}, regular rational readbacks from \autoref{ch:concrete-instances-regseqrat-namecert}, and terminal real seals from \autoref{ch:concrete-instances-real-namecert}. The carrier names only finite filter, net, sequential, separated, transport, replay, provenance, and local naming rows; it does not import quotient completions, representative choice, countable choice, a host complete space, or a global convergence selector.

\begin{definition}[FrechetCompletion carrier]\label{def:frechet-completion-carrier}
A $\FrechetCompletionUp$ carrier is a finite $\BHist$ packet
$$
F=(A,L,N,S,Q,R,H,C,P,K)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the $\CauchyFilterUp$ admission row, recording the finite filter-base observations and Cauchy refinement checks visible to the packet.
\item $L$ is the $\CauchyNetUp$ handoff row, displaying the directed finite net observations that read the same completion route without selecting a cofinal subnet.
\item $N$ is the $\MetricCompletionUp$ neighbour row, exposing only the local completion-facing boundary consumed by later L10 routes.
\item $S$ is the $\SeparatedCompletionUp$ separation row, recording the finite equality and apartness boundary used to prevent two completion reads from being merged by an undisplayed quotient.
\item $Q$ is the paired $\StreamNameUp$ and $\RegSeqRatUp$ sequential readback row, carrying finite windows and regular rational approximants for consumers that ask for a sequence-like presentation.
\item $R$ is the terminal $\RealUp$ seal row for the displayed distance and approximation reads.
\item $H$ records componentwise $\hsame$ transport for the Cauchy filter, Cauchy net, metric-completion neighbour, separated-completion boundary, stream window, regular rational readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
A,L,N,S,Q,R \longmapsto H,P,K .
$$
\item $P$ is the $\Pkg$ provenance over $\FrechetCompletionUp$, $\CauchyFilterUp$, $\CauchyNetUp$, $\MetricCompletionUp$, $\SeparatedCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $K$ is the local $\NameCert_{\FrechetCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,L,N,S,Q,R,H,C,P,K$. It has no coordinate for quotient completion equality, a chosen representative, a countable-choice schedule, a host complete metric space, a selected cofinal subnet, or an ambient convergence oracle.
\end{definition}

\begin{theorem}[FrechetCompletion NameCert obligations]\label{thm:frechet-completion-namecert-obligations}
For every accepted $\FrechetCompletionUp$ carrier
$$
F=(A,L,N,S,Q,R,H,C,P,K),
$$
the local $\NameCert_{\FrechetCompletionUp}$ surface consists exactly of carrier admission for the displayed $\CauchyFilterUp$ row, $\CauchyNetUp$ row, $\MetricCompletionUp$ neighbour row, $\SeparatedCompletionUp$ boundary row, $\StreamNameUp$ and $\RegSeqRatUp$ sequential readback row, $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every public completion read must pass through those rows in the order displayed by $C$.
\end{theorem}
\begin{proof}
Project the accepted carrier in \autoref{def:frechet-completion-carrier}. The visible mathematical rows are the Cauchy filter row $A$, Cauchy net row $L$, local metric-completion neighbour row $N$, separated-completion boundary row $S$, sequential readback row $Q$, and real seal row $R$.

The replay row $C$ orders these rows before transport and naming are read. Thus a public completion-facing consumer first sees the filter and net routes, then the local completion and separation boundaries, and only then the sequential and real readbacks.

The rows $H,P,K$ transport, source, and name exactly this surface. Since the carrier has no coordinate for quotient completion equality, representative choice, countable choice, a selected cofinal subnet, or a host complete space, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[FrechetCompletion filter handoff]\label{thm:frechet-completion-filter-handoff}
Let $F=(A,L,N,S,Q,R,H,C,P,K)$ be an accepted $\FrechetCompletionUp$ carrier. Every downstream completion consumer that enters through the filter side receives a finite handoff through
$$
A \longmapsto L \longmapsto N \longmapsto S \longmapsto Q \longmapsto R \longmapsto H,C,P,K .
$$
The handoff exposes the Cauchy filter row, the matching Cauchy net row, the metric-completion neighbour row, the separated-completion boundary, the sequential readback, the real seal, transport, replay, provenance, and local naming, and it exports no quotient completion, no selected representative, and no choice principle.
\end{theorem}
\begin{proof}
Start with a completion consumer entering through $A$. The carrier makes $A$ a displayed Cauchy-filter row, so the consumer cannot obtain completion data before reading the finite filter-base observations and Cauchy refinement checks.

The net and local completion rows then fix the same route. The row $L$ records the visible net handoff, and $N$ exposes only the local $\MetricCompletionUp$ neighbour boundary rather than a completed host point.

Separation and sequential readback are downstream checks. The row $S$ prevents the route from being collapsed by an undisplayed quotient, while $Q$ and $R$ expose finite stream windows, regular rational approximants, and real seals for consumers that need a sequence-like read.

The structural rows close the handoff. Componentwise transport, displayed replay, provenance, and local naming preserve exactly the route shown above, so no quotient completion, representative selector, or countable-choice coordinate is available.
\end{proof}

\begin{theorem}[FrechetCompletion sequential readback]\label{thm:frechet-completion-sequential-readback}
Every sequence-like read of an accepted $\FrechetCompletionUp$ carrier factors through the displayed $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows after the filter, net, metric-completion, and separated-completion rows have been read. Consequently the sequential presentation is a readback of the finite completion route, not a replacement by a host Cauchy sequence quotient or a selected limit.
\end{theorem}
\begin{proof}
Inspect the accepted carrier. The only sequence-facing coordinate is $Q$, and it is declared as the paired $\StreamNameUp$ and $\RegSeqRatUp$ readback row. The only terminal value-facing coordinate is the $\RealUp$ seal row $R$.

The replay row $C$ places $Q$ and $R$ after the Cauchy filter, Cauchy net, metric-completion neighbour, and separated-completion boundary rows. Thus a sequence-like consumer reads finite windows and rational approximants only as a downstream readback of the displayed completion route.

Because no coordinate stores a host Cauchy sequence quotient, selected limit, representative equality, or ambient completeness theorem, the sequential presentation cannot replace the finite route named by the packet.
\end{proof}

\closureat{FrechetCompletionUp}{seedStr}

\begin{closurestatus}{\FrechetCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:frechet-completion-carrier}, \autoref{thm:frechet-completion-namecert-obligations}, \autoref{thm:frechet-completion-filter-handoff}, and \autoref{thm:frechet-completion-sequential-readback} seed the finite filter-completion packet over Cauchy filter, Cauchy net, metric-completion, separated-completion, sequential readback, real seal, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, representative choice, countable choice, selected cofinal subnets, host complete spaces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, filter handoff, net handoff, metric-completion neighbour routing, separated-completion boundary routing, sequential readback, real seal discipline, transport stability, provenance, and local naming for BEDC.Derived.FrechetCompletionUp.}
  \constructivestory{A $\FrechetCompletionUp$ packet is generated from finite CauchyFilter, CauchyNet, MetricCompletion, SeparatedCompletion, StreamName, RegSeqRat, Real, BHist, hsame, Cont, Pkg, and NameCert rows.}
\end{closurestatus}
