\chapter{A Concrete Naming Certificate for $\OpenBallUp$}
\label{ch:concrete-instances-open-ball-namecert}
\origin{human}

Following Bishop and Bridges and Kelley, the $\OpenBallUp$ packet records the open metric neighbourhood around a displayed centre as finite BEDC NameCert data. It sits after the metric source of \autoref{ch:concrete-instances-metric-namecert}, the real-name and dyadic-radius routes of \autoref{ch:concrete-instances-real-namecert}, the located-distance discipline of \autoref{ch:concrete-instances-locatedmetric-namecert}, and the boundary comparison supplied by \autoref{ch:concrete-instances-metricclosedball-namecert}. The packet gives topology and continuity consumers a reusable neighbourhood row without importing host set openness, quotient point equality, selected radii, compactness, or ambient $\RealUp$ completeness.

\begin{definition}[OpenBall carrier]
\label{def:open-ball-carrier}
An $\OpenBallUp$ carrier is a finite $\BHist$ packet
$$
O=(M,C,R,X,D,B,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricUp$ source row, including the point classifier, metric-distance operation, symmetry, triangle, and zero-distance discipline available from the displayed metric certificate.
\item $C$ is the centre point row, classified as a point of the carrier named by $M$.
\item $R$ is the positive radius row, read either as a $\RealUp$ radius name or as a $\DyadicRatCoreUp$ radius ledger sealed into the $\RealUp$ order surface.
\item $X$ is the point row for the point whose neighbourhood membership is being tested.
\item $D$ is the metric-distance witness row for the displayed distance value $d(C,X)$ over the metric source $M$.
\item $B$ is the distance-below-radius ledger, recording the constructive strict comparison
$$
d(C,X)<_{\mathsf R}R .
$$
\item $H$ records componentwise $\hsame$ transport for the metric source, centre, radius, point, distance witness, strict comparison, replay data, provenance, and local name.
\item $Q$ records displayed $\Cont$ replay of distance evaluation, Real or dyadic radius readback, strict comparison, boundary comparison with $\MetricClosedBallUp$, and neighbourhood handoff to later topology and continuity consumers.
\item $P$ is the $\Pkg$ provenance over $\OpenBallUp$, $\MetricUp$, $\RealUp$, $\DyadicRatCoreUp$, $\LocatedMetricUp$, $\MetricClosedBallUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\OpenBallUp}$ row.
\end{enumerate}
The classifier accepts exactly the rows $M,C,R,X,D,B,H,Q,P,N$. It compares accepted packets only through the displayed metric classifier, radius readback, strict ordered-real comparison, structural transports, replay route, provenance, and local naming row.
\end{definition}

\begin{theorem}[OpenBall NameCert obligations]
\label{thm:open-ball-namecert-obligations}
For an accepted $\OpenBallUp$ carrier
$$
O=(M,C,R,X,D,B,H,Q,P,N),
$$
the local $\NameCert_{\OpenBallUp}$ surface consists exactly of carrier admission, metric-source exposure, centre-point admission, positive radius admission through the $\RealUp$ or $\DyadicRatCoreUp$ route, point admission, distance-witness readback, strict distance-below-radius comparison, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, local naming, and ledger non-escape for the displayed rows $M,C,R,X,D,B,H,Q,P,N$.
\end{theorem}
\begin{proof}
Carrier admission projects the finite packet. The metric source row $M$ supplies the carried point classifier and distance operation, while $C$ and $X$ are admitted only as points over that source.

Radius admission reads $R$ through the displayed real or dyadic route. A dyadic radius is consumed only after its finite ledger is sealed into the ordered $\RealUp$ comparison surface.

The distance and membership obligations are the rows $D$ and $B$. The row $D$ names the distance value $d(C,X)$, and $B$ records the strict comparison $d(C,X)<_{\mathsf R}R$ that makes the point an open-neighbourhood member.

Finally $H,Q,P,N$ transport, replay, source, and name only these rows. Since no other coordinate is present, the packet cannot export host openness, quotient point equality, selected radii, compactness, or ambient real completeness.
\end{proof}

\begin{theorem}[OpenBall metric neighbourhood handoff]
\label{thm:open-ball-metric-neighborhood-handoff}
Every topology or continuity consumer that reads an $\OpenBallUp$ neighbourhood receives the finite route
$$
\MetricUp \longmapsto (C,R,X) \longmapsto D \longmapsto B \longmapsto \NameCert_{\OpenBallUp}.
$$
The handoff factors through the metric source of \autoref{ch:concrete-instances-metric-namecert}, the located-distance discipline of \autoref{ch:concrete-instances-locatedmetric-namecert}, and the boundary comparison of \autoref{ch:concrete-instances-metricclosedball-namecert}; it does not supply a host open set, a generated topology theorem, a compactness argument, a selected limit, or quotient equality of metric points.
\end{theorem}
\begin{proof}
Start with a consumer request for an open metric neighbourhood. The packet first exposes $M$, so the request is tied to the displayed metric carrier and its point classifier before any distance comparison is read.

The centre, radius, and tested point are then the rows $C,R,X$. The located metric route supplies the distance witness $D$, and the strict ledger $B$ turns that witness into the membership comparison.

Boundary comparison with $\MetricClosedBallUp$ is available only as a comparison route in $Q$. The open packet keeps the strict row as the exported neighbourhood witness; the closed-ball chapter remains the sibling non-strict boundary, not a replacement for the open membership comparison.

Thus topology and continuity consumers receive exactly the finite neighbourhood route named by $N$ and replayed by $Q$. The carrier contains no coordinate from which host openness, generated topology closure, compactness, selected limits, or quotient point equality can be recovered.
\end{proof}

\begin{theorem}[OpenBall real-radius boundary]
\label{thm:open-ball-real-radius-boundary}
For an accepted $\OpenBallUp$ packet $O=(M,C,R,X,D,B,H,Q,P,N)$, every radius-sensitive read is exhausted by the positive $\RealUp$ or $\DyadicRatCoreUp$ radius row $R$, the distance witness $D$, and the strict comparison ledger $B$. The packet does not assert completeness of $\RealUp$, trichotomy of real order, a selected rational approximation schedule, or equality of host real values.
\end{theorem}
\begin{proof}
Inspect the radius row $R$. If it is read as a real radius, the packet uses only the displayed ordered-real comparison needed by $B$; if it is read through the dyadic route, the dyadic ledger is first sealed into the same comparison surface.

The distance witness $D$ supplies the other endpoint of the comparison. The membership row is therefore the strict ledger $B$, not a separate real-number construction or a host subset predicate.

Transport through $H$ and replay through $Q$ preserve this finite comparison route. Provenance $P$ and local naming $N$ identify the route as an $\OpenBallUp$ certificate, so no real-completeness theorem, trichotomy oracle, selected approximation schedule, or host equality of real values is exported.
\end{proof}

\closureat{OpenBallUp}{seedStr}

\begin{closurestatus}{\OpenBallUp}
  \constructivestory{An $\OpenBallUp$ packet is generated from a MetricUp source row, a centre point row, a positive RealUp or DyadicRatCoreUp radius row, a point row, a MetricDistanceWitness row, a strict distance-below-radius ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:open-ball-carrier}, \autoref{thm:open-ball-namecert-obligations}, \autoref{thm:open-ball-metric-neighborhood-handoff}, and \autoref{thm:open-ball-real-radius-boundary} seed the finite open-neighbourhood route over metric distance and positive real or dyadic radius data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host set openness, generated topology closure, compactness, quotient equality for metric points, selected radii, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, metric-source exposure, positive-radius admission, distance-witness readback, strict comparison transport, neighbourhood handoff, real-radius boundary, and ledger non-escape for BEDC.Derived.OpenBallUp.}
\end{closurestatus}
