\chapter{A Concrete Naming Certificate for $\CompactUniformContinuitySchemeUp$}
\label{ch:concrete-instances-compact-uniform-continuity-scheme-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CompactUniformContinuitySchemeUp$ packet names the complete finite-net route by which compact metric data and continuous-map pointwise moduli yield a uniform-modulus ledger. It consumes the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the metric triangle surface of \autoref{ch:concrete-instances-metric-namecert}, the finite rational lower-bound fold of \autoref{ch:concrete-instances-finitenetminimumfold-namecert}, the uniform-modulus consumer row of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the rational tolerance source of \autoref{ch:concrete-instances-rat-namecert}. The scheme records the Heine--Cantor proof as one BEDC packet, with no appeal to open-cover compactness, a host modulus selector, or choice.

\begin{definition}[Compact uniform-continuity scheme carrier]
\label{def:compact-uniform-continuity-scheme-carrier}
A $\CompactUniformContinuitySchemeUp$ carrier is a finite $\BHist$ packet
$$
U=(X,Y,F,E,P,M,Q,T,G,H,R,S,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the $\CompactMetricUp$ source row, including the finite $\mathsf{ProbeBundle}$ net surface used at the requested tolerance.
\item $Y$ is the target $\MetricUp$ row whose triangle ledger reads the final estimate.
\item $F$ is the $\ContinuousMapUp$ graph and pointwise-modulus row from $X$ to $Y$.
\item $E$ is the positive $\RatUp$ tolerance row, including the rational subdivision data used for the source and target triangle estimates.
\item $P$ is the finite center bundle supplied by the compact metric row.
\item $M$ is the pointwise-modulus ledger at the centers of $P$.
\item $Q$ is the subordinate-radius ledger binding each center radius to the pointwise-modulus precision at that center.
\item $T$ is the $\FiniteNetMinimumFoldUp$ lower-bound fold over the finite radius ledger.
\item $G$ is the $\UniformModulusUp$ consumer row produced from $E,T,M,Q$ and the metric triangle ledgers of $X$ and $Y$.
\item $H$ records componentwise $\hsame$ transport for the compact source, target metric, continuous map, tolerance row, center bundle, pointwise rows, subordinate radii, finite fold, uniform-modulus handoff, replay, provenance, and local naming.
\item $R$ records displayed $\Cont$ replay from a uniform-modulus request through $X,Y,F,E,P,M,Q,T,G,H,S,N$.
\item $S$ is the $\Pkg$ provenance over $\CompactUniformContinuitySchemeUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\MetricUp$, $\FiniteNetMinimumFoldUp$, $\UniformModulusUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactUniformContinuitySchemeUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $X,Y,F,E,P,M,Q,T,G,H,R,S,N$. It contains no open-cover compactness coordinate, selected Lebesgue-number proof, host modulus function, countable-choice schedule, or ambient completeness theorem.
\end{definition}

\begin{theorem}[Compact uniform-continuity scheme NameCert obligations]
\label{thm:compact-uniform-continuity-scheme-namecert-obligations}
For every accepted $\CompactUniformContinuitySchemeUp$ carrier $U=(X,Y,F,E,P,M,Q,T,G,H,R,S,N)$, the local $\NameCert_{\CompactUniformContinuitySchemeUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed compact source, target metric, continuous-map ledger, positive rational tolerance, finite center bundle, pointwise-modulus rows, subordinate-radius ledger, finite lower-bound fold, uniform-modulus handoff, transport, replay, provenance, and local naming rows;
\item source lock, requiring the compact metric row $X$ and continuous-map source row in $F$ to expose the same metric carrier before any center or modulus row is read;
\item finite-net extraction, requiring the centers in $P$ and coverage rows in $X$ to be the only compactness data consumed by the scheme;
\item pointwise-modulus binding, requiring each row of $M$ and $Q$ to attach to a displayed center of $P$ and to the same rational tolerance row $E$;
\item rational-fold exactness, requiring $T$ to be the finite $\RatUp$ lower-bound fold over the displayed subordinate radii rather than an external minimum selector;
\item uniform-modulus handoff, requiring $G$ to be obtained from the finite fold, pointwise rows, and source and target metric triangle ledgers;
\item ledger nonescape, excluding open-cover compactness, selected Lebesgue numbers, host modulus functions, choice, sequential compactness, and ambient completeness as local certificate data.
\end{enumerate}
No compact uniform-continuity scheme obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:compact-uniform-continuity-scheme-carrier}. The analytic rows are the compact source $X$, target metric $Y$, continuous-map ledger $F$, rational tolerance $E$, center bundle $P$, pointwise rows $M$, subordinate radii $Q$, rational fold $T$, and uniform-modulus handoff $G$.

The source lock is forced before any compact-continuity read. The compact metric row and the continuous-map source row are the same displayed metric carrier, so the center rows and pointwise-modulus rows cannot be read over different sources.

The finite-net and pointwise-modulus obligations are rowwise. The bundle $P$ supplies the centers, $M$ supplies the local modulus rows at those centers, and $Q$ attaches each subordinate radius to the corresponding local precision.

The lower-bound fold $T$ is the quantitative step. Since it is carried by $\FiniteNetMinimumFoldUp$ over the displayed $\RatUp$ radii, the scheme exports a classifier-stable precision history rather than a host-selected minimum.

Finally $G$ reads the source and target triangle ledgers through $X$ and $Y$ and packages the result as a $\UniformModulusUp$ row. The structural rows $H,R,S,N$ replay only the displayed route, so open-cover compactness, selected Lebesgue numbers, host modulus functions, choice, and ambient completeness have no coordinate from which to enter the local certificate.
\end{proof}

\begin{theorem}[Compact uniform-continuity scheme handoff]
\label{thm:compact-uniform-continuity-scheme-handoff}
Every $\UniformModulusUp$ consumer reading an accepted $\CompactUniformContinuitySchemeUp$ carrier factors through the finite route
$$
X,F,E \longmapsto P,M,Q,T \longmapsto G,H,R,S,N .
$$
Thus the consumer receives compact finite-net data, continuous-map pointwise-modulus rows, rational subordinate-radius rows, the finite lower-bound fold, and the metric-triangle estimate before the uniform-modulus row is public. The handoff exports no open-cover compactness, selected Lebesgue number, host modulus selector, countable-choice schedule, sequential compactness argument, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with a uniform-modulus consumer of $U$. By \autoref{def:compact-uniform-continuity-scheme-carrier}, the consumer first reads the compact source $X$, the continuous-map row $F$, and the rational tolerance $E$.

The finite compactness and continuity data are opened next. The center bundle $P$ comes from the compact metric row, the pointwise rows $M$ come from the continuous-map ledger at those centers, and the subordinate-radius ledger $Q$ binds the two surfaces to the same tolerance request.

The lower-bound fold $T$ then computes the tolerance-only precision history over the displayed finite rational radius ledger. The handoff row $G$ applies the metric triangle rows in the source and target metrics and records the result as a $\UniformModulusUp$ row.

The transport, replay, provenance, and local naming rows expose exactly this finite route. Applying \autoref{thm:compact-uniform-continuity-scheme-namecert-obligations}, the consumer cannot replace it by an open-cover proof, a selected Lebesgue number, an external modulus function, countable choice, sequential compactness, or ambient completeness.
\end{proof}

\closureat{CompactUniformContinuitySchemeUp}{seedStr}

\begin{closurestatus}{\CompactUniformContinuitySchemeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-continuity-scheme-carrier}, \autoref{thm:compact-uniform-continuity-scheme-namecert-obligations}, and \autoref{thm:compact-uniform-continuity-scheme-handoff} seed the compact-uniform-continuity proof scheme over compact metric finite nets, continuous-map pointwise moduli, rational subordinate radii, finite lower-bound folds, metric triangle ledgers, uniform-modulus handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected Lebesgue numbers, host modulus functions, sequential compactness, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source lock, finite-net extraction, pointwise-modulus binding, rational-fold exactness, uniform-modulus handoff, and ledger nonescape for BEDC.Derived.CompactUniformContinuitySchemeUp.}
  \constructivestory{A $\CompactUniformContinuitySchemeUp$ packet is generated from CompactMetricUp source finite-net rows, a target MetricUp row, ContinuousMapUp pointwise-modulus rows, a positive RatUp tolerance, subordinate center radii, a FiniteNetMinimumFoldUp lower-bound fold, a UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
