\chapter{A Concrete Naming Certificate for $\EulerTransformUp$}
\label{ch:concrete-instances-euler-transform-namecert}
\origin{human}

Following Euler and Hardy on divergent series and Bishop--Bridges constructive analysis, the $\EulerTransformUp$ packet records finite Euler acceleration for alternating real series as a displayed BEDC route. It consumes the source-series surface of \autoref{ch:concrete-instances-realseries-namecert}, the alternating-sign route of \autoref{ch:concrete-instances-alternating-series-test-namecert}, the Abel and Dirichlet neighboring handoffs of \autoref{ch:concrete-instances-abel-test-namecert} and \autoref{ch:concrete-instances-dirichlet-test-namecert}, the summable tail budget of \autoref{ch:concrete-instances-summable-tail-modulus-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a finite acceleration boundary for Real and Completion series consumers; it is not a host infinite sum, selected limit, quotient series equality, classical convergence transfer, ambient completeness theorem, Lean verification, or bridge checking.

\begin{definition}[Euler transform carrier]\label{def:euler-transform-carrier}
An $\EulerTransformUp$ carrier is a finite $\BHist$ packet
$$
E=(S,A,D,T,B,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\RealSeriesUp$ row, exposing only the inspected real-series windows and partial-sum windows used by the current alternating-tail request.
\item $A$ is the alternating-sign row, recording the finite parity and sign windows consumed by the $\AlternatingSeriesTestUp$ surface.
\item $D$ is the finite forward-difference triangle, displaying the finitely many iterated difference rows used by the Euler acceleration step.
\item $T$ is the transformed tail-window row, naming the accelerated tail windows obtained from $S,A,D$.
\item $B$ is the summable tail and modulus budget, requiring the transformed windows to be served through $\SummableTailModulusUp$ before any endpoint read is available.
\item $R$ is the $\RegSeqRatUp$ handoff reached only after the transformed tail windows and the summable budget have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source, alternating, difference, transformed-window, budget, readback, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a tail request through $D,T,B,R$.
\item $P$ is the $\Pkg$ provenance over $\EulerTransformUp$, $\RealSeriesUp$, $\AlternatingSeriesTestUp$, $\AbelTestUp$, $\DirichletTestUp$, $\SummableTailModulusUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\EulerTransformUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,A,D,T,B,R,H,C,P,N$. It has no coordinate for host infinite sums, selected limits, quotient series equality, classical convergence transfer, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Euler transform NameCert obligations]\label{thm:euler-transform-namecert-obligations}
For every accepted $\EulerTransformUp$ carrier
$$
E=(S,A,D,T,B,R,H,C,P,N),
$$
the local $\NameCert_{\EulerTransformUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the source $\RealSeriesUp$ row, alternating-sign row, finite forward-difference triangle, transformed tail windows, summable tail budget, $\RegSeqRatUp$ handoff, transport, replay, provenance, and local naming row;
\item alternating-window exactness, requiring $A$ to supply the only sign and parity data used by the acceleration step;
\item difference-triangle stability, requiring each displayed forward-difference row in $D$ to be read from the same finite source windows in $S$ and transported componentwise by $H$;
\item transformed-tail coherence, requiring $T$ to name only windows obtained from the displayed difference triangle and alternating route;
\item budget service, requiring $B$ to provide the summable tail and modulus boundary before the regular rational handoff $R$ can be consumed;
\item neighboring-test discipline, requiring Abel and Dirichlet rows to appear only as provenance faces for the same tail-window route and not as independent endpoint seals;
\item nonescape, requiring $H,C,P,N$ to transport, replay, source, and name exactly this route and no unrecorded analytic principle.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:euler-transform-carrier}. The visible inventory is $S,A,D,T,B,R,H,C,P,N$, so the local certificate has no detached row for a host sum, selected limit, quotient equality, classical convergence transfer, or ambient completeness theorem.

The alternating and difference data are read before any transformed endpoint is available. The row $A$ supplies the finite sign and parity windows, while $D$ displays only the forward-difference triangle computed from the same inspected source windows in $S$.

The transformed-tail row is then forced through $T$. It can name only acceleration windows obtained from $S,A,D$, and the summable tail budget $B$ is the only row that turns those windows into a modulus-bearing endpoint service.

Finally, $R,H,C,P,N$ supply regular readback, transport, replay, provenance, and local naming for the same route. The Abel and Dirichlet faces appear only in the provenance of the shared tail-window discipline, so no independent endpoint seal or stronger convergence principle is exported.
\end{proof}

\begin{theorem}[Euler transform alternating acceleration handoff]\label{thm:euler-transform-alternating-acceleration-handoff}
Every endpoint-facing read of an accepted $\EulerTransformUp$ carrier factors through the ordered route
$$
\RealSeriesUp \longmapsto \AlternatingSeriesTestUp \longmapsto \SummableTailModulusUp \longmapsto \RegSeqRatUp \longmapsto \RealUp.
$$
The Abel and Dirichlet rows may be read only as neighboring provenance for the same transformed tail-window route. No endpoint-facing consumer reaches $\RegSeqRatUp$ or $\RealUp$ before the finite forward-difference triangle and summable tail budget have been displayed.
\end{theorem}
\begin{proof}
Start from the accepted carrier $E=(S,A,D,T,B,R,H,C,P,N)$. The only source row is $S$, and the only alternating information is the sign-window row $A$.

The acceleration handoff is carried by $D$ and $T$. The finite difference triangle is read from the displayed source windows, and the transformed tail windows are the only rows passed downstream.

The budget row $B$ supplies the summable tail and modulus service for those transformed windows. Only after that service appears may the route enter $R$ and then the terminal $\RealUp$ read. Since Abel and Dirichlet data occur only inside the provenance row $P$, they cannot replace the displayed alternating, difference, budget, or regular-rational rows.
\end{proof}

\begin{theorem}[Euler transform Real seal nonescape]\label{thm:euler-transform-real-seal-nonescape}
For every accepted $\EulerTransformUp$ carrier $E=(S,A,D,T,B,R,H,C,P,N)$, any consumer that reaches a $\RealUp$ endpoint seal without the displayed source-series windows, alternating-sign row, finite forward-difference triangle, transformed tail windows, summable tail budget, and $\RegSeqRatUp$ handoff has left the local $\NameCert_{\EulerTransformUp}$ surface.
\end{theorem}
\begin{proof}
Read the obligation rows in \autoref{thm:euler-transform-namecert-obligations}. Endpoint-facing data must pass through carrier exposure, alternating-window exactness, difference-triangle stability, transformed-tail coherence, budget service, regular readback, transport, replay, provenance, and naming.

The only Real-facing route named by the carrier is downstream of $R$. Therefore a consumer that omits any of $S,A,D,T,B,R$ is asking for a row absent from the carrier and absent from the local certificate. The rows $H,C,P,N$ preserve the same route rather than adding host sums, selected limits, quotient equality, classical convergence transfer, ambient completeness, Lean verification, or bridge data.
\end{proof}

\falsifiablePrediction{Every accepted $\EulerTransformUp$ endpoint-facing read factors through source RealSeries windows, alternating-sign windows, a finite forward-difference triangle, transformed tail windows, a SummableTailModulus budget, RegSeqRat readback, Real sealing, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{realseries, alternating-series-test, abel-test, dirichlet-test, summable-tail-modulus, regseqrat, real: $\EulerTransformUp$ is not bijective to any listed sibling because it jointly carries source series windows, alternating signs, finite forward differences, transformed tail windows, summable tail budgets, regular rational readback, transport, replay, provenance, and local naming.}

\closureat{EulerTransformUp}{seedStr}

\begin{closurestatus}{\EulerTransformUp}
  \constructivestory{An $\EulerTransformUp$ packet is generated from source RealSeries windows, alternating-sign rows, a finite forward-difference triangle, transformed tail windows, a SummableTailModulus budget, RegSeqRat readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:euler-transform-carrier}, \autoref{thm:euler-transform-namecert-obligations}, \autoref{thm:euler-transform-alternating-acceleration-handoff}, and \autoref{thm:euler-transform-real-seal-nonescape} seed the finite Euler acceleration boundary over displayed source series, alternating signs, forward differences, transformed tail budgets, $\RegSeqRatUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, selected limits, quotient series equality, classical convergence transfer, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean theorems for carrier exposure, alternating-window exactness, difference-triangle stability, transformed-tail coherence, summable budget service, regular-rational handoff, Real seal nonescape, and transport, replay, provenance, and local naming discipline for BEDC.Derived.EulerTransformUp.}
\end{closurestatus}
