\chapter{A Concrete Naming Certificate for $\StronglyExtensionalRealMapUp$}
\label{ch:concrete-instances-strongly-extensional-real-map-namecert}
\origin{human}

Following Bishop and Bridges, strongly extensional maps on real names are read as graph certificates that preserve apartness and RegSeqRat classifier data. The $\StronglyExtensionalRealMapUp$ packet connects the regular Cauchy real-name surface of \autoref{ch:concrete-instances-real-namecert}, the rational readback discipline of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. It records only displayed finite graph rows and transport obligations; it is not a host real function, a quotient-function equality, a trichotomy principle, an open-cover compactness object, or an ambient $\RealUp$ completeness theorem.

\begin{definition}[Strongly extensional real-map carrier]
\label{def:strongly-extensional-real-map-carrier}
A $\StronglyExtensionalRealMapUp$ carrier is a finite $\BHist$ packet
$$
F=(X,Y,G,A,S,R,D,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source $\RealUp$ name row, including its regular Cauchy presentation and finite observation boundary.
\item $Y$ is the target $\RealUp$ name row reached after the displayed graph route is consumed.
\item $G$ is the finite graph certificate, pairing inspected source windows with inspected target windows.
\item $A$ is the apartness-preservation ledger: every displayed apartness witness between source names is routed to a displayed apartness witness between target names.
\item $S$ is the $\StreamNameUp$ window family opened by the graph certificate before any regular rational readback is taken.
\item $R$ is the $\RegSeqRatUp$ classifier-readback row attached to the source and target windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare the displayed rational approximants and apartness margins.
\item $H$ records componentwise $\hsame$ transport for the two real-name rows, graph row, apartness ledger, stream windows, rational readbacks, dyadic tolerances, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
X,G,S,R,D \longmapsto Y,A,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\StronglyExtensionalRealMapUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StronglyExtensionalRealMapUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,G,A,S,R,D,H,C,P,N$. It has no coordinate for host functions, quotient equality of real names, trichotomy, open-cover compactness, or ambient completeness.
\end{definition}

\begin{theorem}[Strongly extensional real-map NameCert obligations]
\label{thm:strongly-extensional-real-map-namecert-obligations}
For every accepted $\StronglyExtensionalRealMapUp$ carrier $F=(X,Y,G,A,S,R,D,H,C,P,N)$, the local $\NameCert_{\StronglyExtensionalRealMapUp}$ surface consists exactly of carrier exposure, source and target real-name exposure, graph-window exactness, apartness-preservation exposure, $\StreamNameUp$ window discipline, $\RegSeqRatUp$ classifier readback, $\DyadicRatCoreUp$ tolerance service, classifier transport, and non-escape of host functions, quotient equality, trichotomy, open-cover compactness, and ambient $\RealUp$ completeness. Every obligation is read from $X,Y,G,A,S,R,D,H,C,P,N$ and their displayed $\hsame$ and $\Cont$ routes.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:strongly-extensional-real-map-carrier}. The visible inventory is exactly the two real-name rows, graph row, apartness ledger, stream windows, regular rational readbacks, dyadic tolerance ledger, transport, replay, provenance, and local naming.

Graph-window exactness is forced through $G$ and $S$: each inspected source window is paired with a displayed target window before any target real-name row is consumed. The apartness-preservation obligation is the row $A$, and it records only displayed apartness witnesses rather than a global host-function property.

Regular rational classifier data then pass through $R$, while dyadic tolerance comparisons pass through $D$. Transport by $H$ and replay by $C$ preserve the same finite route, and $P,N$ source and name it locally. Since no carrier coordinate names a host function, quotient equality, trichotomy, compact cover, or ambient completeness theorem, none can be exported by the local certificate.
\end{proof}

\begin{theorem}[Strongly extensional real-map RegSeqRat transport]
\label{thm:strongly-extensional-real-map-regseqrat-transport}
Every $\RegSeqRatUp$ consumer of an accepted $\StronglyExtensionalRealMapUp$ carrier factors through the finite chain
$$
\RealUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp
$$
together with the graph row $G$, apartness ledger $A$, and structural rows $H,C,P,N$. If two displayed source reads are classifier-equal on the same finite regular Cauchy window, then their transported target reads are compared only by the corresponding $\RegSeqRatUp$ row and dyadic tolerance ledger in the carrier. The theorem does not assert equality of host functions or equality of ambient real-number quotients.
\end{theorem}
\begin{proof}
Start from the accepted carrier $F=(X,Y,G,A,S,R,D,H,C,P,N)$. A regular-rational consumer first reads the source real-name row $X$ and then the stream windows $S$ selected by the graph certificate $G$.

The classifier readback is the row $R$. Any comparison of source reads on the same finite regular Cauchy window must therefore pass through the displayed $\RegSeqRatUp$ classifier data before reaching a target read.

The dyadic tolerance ledger $D$ supplies the numeric comparison margins, while the apartness ledger $A$ records the strongly extensional direction on displayed witnesses. The structural rows $H,C,P,N$ transport, replay, source, and name the same route, so the transported target comparison remains a finite RegSeqRat-and-dyadic read rather than a host-function equality or quotient-real equality.
\end{proof}

\closureat{StronglyExtensionalRealMapUp}{seedStr}

\begin{closurestatus}{\StronglyExtensionalRealMapUp}
  \constructivestory{A $\StronglyExtensionalRealMapUp$ packet is generated from source and target RealUp name rows, a finite graph certificate, an apartness-preservation ledger, StreamName windows, RegSeqRat classifier readback, a DyadicRatCore tolerance ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:strongly-extensional-real-map-carrier}, \autoref{thm:strongly-extensional-real-map-namecert-obligations}, and \autoref{thm:strongly-extensional-real-map-regseqrat-transport} seed the finite graph-certificate route for strongly extensional maps on regular Cauchy real names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close $\RealUp$ completeness, host function equality, quotient equality of real names, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, graph-window exactness, apartness-preservation exposure, StreamName window discipline, RegSeqRat classifier transport, DyadicRatCore tolerance service, and non-escape for BEDC.Derived.StronglyExtensionalRealMapUp.}
\end{closurestatus}
