\chapter{A Concrete Naming Certificate for $\CantorCompleteMetricUp$}
\label{ch:concrete-instances-cantor-complete-metric-namecert}
\origin{human}

Following Cantor's intersection theorem and Bishop--Bridges constructive metric completion, the $\CantorCompleteMetricUp$ packet records the nested closed-ball criterion for reading a complete-metric point from finite BEDC data. It sits after the complete-metric surface of \autoref{ch:concrete-instances-completemetric-namecert}, the completion route of \autoref{ch:concrete-instances-metriccompletion-namecert}, the Cauchy-filter interface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the nested-interval spine of \autoref{ch:concrete-instances-nestedinterval-namecert}, and the L10 real-name route through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names a constructive closed-ball handoff; it does not import open-cover compactness, countable choice, quotient completions, selected limits, or full $\RealUp$ completeness.

\begin{definition}[CantorCompleteMetric carrier]
\label{def:cantor-complete-metric-carrier}
A $\CantorCompleteMetricUp$ carrier is a finite $\BHist$ packet
$$
K_{\mathrm{ccm}}=(M,B,F,D,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\CompleteMetricUp$ source row whose metric and convergence obligations are the only complete-metric data available to the packet.
\item $B$ is the nested closed-ball row, listing a descending finite window of closed metric balls with each later ball displayed inside the earlier ball.
\item $F$ is the $\CauchyFilterUp$ row generated by the nested ball spine and read only through the displayed ball inclusions.
\item $D$ is the $\DyadicRatCoreUp$ radius ledger, storing the requested tolerances and the visible shrink bounds for the ball radii.
\item $W$ is the $\StreamNameUp$ finite-window row selecting the inspected nested-ball prefix.
\item $Q$ is the $\RegSeqRatUp$ readback row that exposes the numerical radius and center schedule needed by the completion route.
\item $E$ is the $\RealUp$ seal reached only after $B,F,D,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the metric source, nested closed balls, Cauchy filter, dyadic radius ledger, finite windows, regular readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from closed-ball inclusion through Cauchy-filter generation, dyadic radius shrinkage, finite windows, regular readback, and the terminal real seal.
\item $P$ is the $\Pkg$ provenance over $\CantorCompleteMetricUp$, $\CompleteMetricUp$, $\MetricCompletionUp$, $\CauchyFilterUp$, $\NestedIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CantorCompleteMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. There is no coordinate for an open cover, a countable-choice selector, a quotient completion, a selected limit, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CantorCompleteMetric NameCert obligations]
\label{thm:cantor-complete-metric-namecert-obligations}
For every accepted $\CantorCompleteMetricUp$ carrier
$$
K_{\mathrm{ccm}}=(M,B,F,D,W,Q,E,H,C,P,N),
$$
the local $\NameCert_{\CantorCompleteMetricUp}$ surface consists exactly of carrier admission, nested closed-ball inclusion, radius shrinkage, Cauchy-filter generation, finite-window exposure, regular-rational readback, terminal $\RealUp$ sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming over the rows displayed in \autoref{def:cantor-complete-metric-carrier}. It has no obligation row for open-cover compactness, countable choice, quotient completions, selected limits, or full $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier $K_{\mathrm{ccm}}$. The row $M$ supplies only the complete-metric source already named by \autoref{ch:concrete-instances-completemetric-namecert}, while $B$ supplies the nested closed-ball spine and $F$ repacks that spine as the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}.

The radius data are read next. The dyadic ledger $D$ records the visible shrink bounds, and the finite window $W$ determines which closed balls are inspected at the requested tolerance.

The numerical readback and seal are downstream. The row $Q$ exposes the regular-rational schedule used by \autoref{ch:concrete-instances-regseqrat-namecert}, and the row $E$ seals that read as the $\RealUp$ output only after the nested-ball and filter rows have been displayed.

The structural rows $H,C,P,N$ preserve the same route. Since no row contains an open cover, a countable-choice selector, a quotient completion, a selected limit, or full $\RealUp$ completeness data, none of those objects can become a local NameCert obligation.
\end{proof}

\begin{theorem}[CantorCompleteMetric nested closed-ball handoff]
\label{thm:cantor-complete-metric-nested-ball-handoff}
Every completion-facing read exported by an accepted $\CantorCompleteMetricUp$ carrier factors through the finite route
$$
M,B \longmapsto F,D,W \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus a later $\CompactMetricUp$ or Real-and-Completion consumer receives the $\CompleteMetricUp$ source row, descending closed-ball window, $\CauchyFilterUp$ handoff, dyadic radius ledger, finite $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealUp$ seal, transport, replay, provenance, and local $\NameCert$ rows. The route exports no open-cover compactness, countable choice, quotient completion, selected limit, or full $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Begin with a completion-facing consumer request. The request can inspect the packet only through the accepted carrier, so the first visible data are the complete-metric row $M$ and the nested closed-ball spine $B$.

The handoff then passes through the generated filter and radius ledger. The row $F$ records the Cauchy-filter surface coming from the nested balls, while $D$ and $W$ bind each tolerance request to a displayed finite window.

The regular-rational readback follows the same finite route. The row $Q$ is read after the ball, filter, radius, and window rows, and $E$ seals only that displayed read as the Real-facing output.

Finally $H,C,P,N$ transport, replay, source, and name the route. No step opens an open cover, chooses countably many centers, quotients a completion, selects a host limit, or invokes full $\RealUp$ completeness.
\end{proof}

\closureat{CantorCompleteMetricUp}{seedStr}

\begin{closurestatus}{\CantorCompleteMetricUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cantor-complete-metric-carrier}, \autoref{thm:cantor-complete-metric-namecert-obligations}, and \autoref{thm:cantor-complete-metric-nested-ball-handoff} seed the finite nested closed-ball criterion for complete-metric consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, countable choice, quotient completions, selected limits, full $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nested closed-ball inclusion, radius shrinkage, Cauchy-filter generation, finite-window exposure, regular readback, Real sealing, transport, replay, provenance, local naming, and TasteGate field faithfulness for BEDC.Derived.CantorCompleteMetricUp.}
  \constructivestory{A $\CantorCompleteMetricUp$ packet is generated from a CompleteMetric source row, descending closed-ball window, CauchyFilter handoff, DyadicRatCore radius ledger, StreamName window, RegSeqRat readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
