\chapter{A Concrete Naming Certificate for $\NormalFamilyUp$}
\label{ch:concrete-instances-normal-family-namecert}
\origin{human}

Following Montel and Arzela--Ascoli, the $\NormalFamilyUp$ packet names the finite compact-continuity surface used to read a normal family of maps from a compact metric source into a complete metric target. It consumes the $\ArzelaAscoliUp$ handoff of \autoref{ch:concrete-instances-arzelaascoli-namecert}, the compact source rows of \autoref{ch:concrete-instances-compactmetric-namecert}, the complete target rows of \autoref{ch:concrete-instances-completemetric-namecert}, the continuous-map family rows of \autoref{ch:concrete-instances-continuousmap-namecert}, and the pointwise image rows of $\TotallyBoundedUp$ as finite carrier data.

The chapter records the normal-family object as a naming certificate surface, not as an ambient compact-open topology, a selected convergent subsequence, or a choice principle. Every consumer read must pass through the displayed family ledger, compact source net, complete target ledger, equicontinuity rows, pointwise total-bounded image rows, finite $\mathsf{ProbeBundle}$ net data, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row.

\begin{definition}[Normal-family carrier]
\label{def:normal-family-carrier}
A $\NormalFamilyUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
N=(F,X,Y,M,E,I,Q,H,C,P,L)
$$
with the following visible coordinates:
\begin{enumerate}
\item $F$ is the finite family ledger whose entries are $\ContinuousMapUp$ rows from the source row $X$ to the target row $Y$;
\item $X$ is the compact source row, read through $\CompactMetricUp$ and its finite $\mathsf{ProbeBundle}$ net surface;
\item $Y$ is the complete target row, read through $\CompleteMetricUp$ and its displayed limit-witness ledgers;
\item $M$ is the compact-continuity handoff row supplied by $\ArzelaAscoliUp$ for the same source, target, and family ledger;
\item $E$ records equicontinuity rows binding target tolerances to finite source-radius rows uniformly over $F$;
\item $I$ records pointwise $\TotallyBoundedUp$ image rows for the displayed target values over the bundled source probes;
\item $Q$ records the finite $\mathsf{ProbeBundle}$ net data used by the compact source and by the Arzela--Ascoli handoff;
\item $H$ records componentwise $\hsame$ transport for the family ledger, compact source, complete target, equicontinuity rows, pointwise image rows, probe rows, and handoff row;
\item $C$ records the displayed $\Cont$ replay routes for compact-metric, complete-metric, continuous-map, total-bounded, and Arzela--Ascoli consumers;
\item $P$ is the $\Pkg$ provenance over $\NormalFamilyUp$, $\ArzelaAscoliUp$, $\CompactMetricUp$, $\CompleteMetricUp$, $\ContinuousMapUp$, $\TotallyBoundedUp$, $\mathsf{ProbeBundle}$, $\hsame$, and $\Cont$ rows;
\item $L$ is the local $\NameCert_{\NormalFamilyUp}$ row.
\end{enumerate}
The packet contains no host function-space carrier, open-cover compactness row, selected subsequence, ambient holomorphic-function principle, or choice-selected cluster point.
\end{definition}

\begin{theorem}[Normal-family NameCert obligations]
\label{thm:normal-family-namecert-obligations}
The local $\NameCert_{\NormalFamilyUp}$ surface consists exactly of carrier admission for the packet of \autoref{def:normal-family-carrier}; classifier transport of the family ledger, compact source, complete target, Arzela--Ascoli handoff, equicontinuity rows, pointwise total-bounded image rows, finite probe rows, and displayed provenance; and non-escape through the recorded $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.
\end{theorem}
\begin{proof}
Carrier admission is the displayed tuple $N=(F,X,Y,M,E,I,Q,H,C,P,L)$. Each analytic coordinate is visible before the local certificate may be read: the family ledger $F$, compact source $X$, complete target $Y$, Arzela--Ascoli handoff $M$, equicontinuity rows $E$, pointwise image rows $I$, and probe rows $Q$.

Classifier transport is componentwise. The $\ContinuousMapUp$ rows transport the family graph data, the $\CompactMetricUp$ row transports source finite-net data, the $\CompleteMetricUp$ row transports target limit ledgers, and the $\TotallyBoundedUp$ rows transport pointwise image bundles.

The remaining rows $H,C,P,L$ preserve the same coordinates under $\hsame$ transport, replay them through displayed $\Cont$ routes, record their $\Pkg$ provenance, and name the packet locally. Since no omitted coordinate names a host function space, open-cover compactness, selected subsequence, or choice-selected cluster point, the certificate exports only the displayed normal-family surface.
\end{proof}

\begin{theorem}[Normal-family Arzela-Ascoli handoff]
\label{thm:normal-family-arzela-ascoli-handoff}
Every compact-continuity consumer reading an accepted $\NormalFamilyUp$ packet factors through the $\ArzelaAscoliUp$ row $M$, the compact source row $X$, the complete target row $Y$, the continuous-map family ledger $F$, the equicontinuity rows $E$, the pointwise $\TotallyBoundedUp$ image rows $I$, the finite $\mathsf{ProbeBundle}$ data $Q$, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.

Consequently the handoff supplies the finite data needed for the constructive normal-family reading and supplies no ambient compact-open topology, open-cover compactness principle, selected subsequence, or host choice principle.
\end{theorem}
\begin{proof}
Project the Arzela--Ascoli coordinate $M$. Its role is only to consume the same compact source, complete target, family ledger, equicontinuity rows, pointwise image rows, and finite probe rows already displayed in the $\NormalFamilyUp$ carrier.

Next read $X,Y,F,E,I,Q$. These rows provide the compact source net, the complete target ledger, the continuous-map family entries, the uniform equicontinuity witnesses, the pointwise total-bounded image bundles, and the probe data that the handoff needs.

Finally attach $H,C,P,L$. They ensure that every downstream read uses the transported and replayed carrier rows rather than an ambient function-space object. The absence of any further coordinate rules out open-cover compactness, selected subsequences, and host choice.
\end{proof}

\closureat{NormalFamilyUp}{seedStr}

\begin{closurestatus}{\NormalFamilyUp}
  \constructivestory{A $\NormalFamilyUp$ packet is generated from a finite family ledger, compact source row, complete target row, Arzela-Ascoli handoff row, equicontinuity rows, pointwise total-bounded image rows, finite ProbeBundle net data, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:normal-family-carrier}, \autoref{thm:normal-family-namecert-obligations}, and \autoref{thm:normal-family-arzela-ascoli-handoff} seed the finite normal-family certificate over ArzelaAscoliUp, CompactMetricUp, CompleteMetricUp, ContinuousMapUp, TotallyBoundedUp, ProbeBundle, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, ambient compact-open topology, open-cover compactness, selected subsequences, holomorphic compactness, or host choice.}
  \upgradepath{Obligation closure requires checked carrier projection, classifier transport, Arzela-Ascoli handoff confinement, provenance replay, and local naming for the $\NormalFamilyUp$ packet.}
\end{closurestatus}
