\chapter{A Concrete Naming Certificate for $\UniformLimitTheoremUp$}
\label{ch:concrete-instances-uniform-limit-theorem-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\UniformLimitTheoremUp$ packet records the finite NameCert route by which a uniformly convergent sequence of continuous maps exports continuity of its limit. It consumes the continuous-map rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the uniform-limit ledger of \autoref{ch:concrete-instances-uniformlimit-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seals of \autoref{ch:concrete-instances-real-namecert}, and the metric source and target rows of \autoref{ch:concrete-instances-metric-namecert}. The packet names the theorem handoff as finite certificate data; it is not an ambient function-space topology, a quotient stream equality, a selected host limit, or a global completeness principle for $\RealUp$.

\begin{definition}[Uniform-limit theorem carrier]
\label{def:uniform-limit-theorem-carrier}
A $\UniformLimitTheoremUp$ carrier is a finite $\BHist$ packet
$$
U=(F,L,W,R,E,X,Y,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\ContinuousMapUp$ sequence ledger. Each entry records a continuous map from the displayed metric source $X$ to the displayed metric target $Y$.
\item $L$ is the $\UniformLimitUp$ modulus ledger binding target tolerances to a finite tail stage and to the shared source-radius information used by the limit read.
\item $W$ is the $\StreamNameUp$ window family exposing exactly the finite values of the sequence and of the limit candidate needed for the displayed tolerance request.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the windows in $W$ after the uniform-limit budget in $L$ has fixed the tail.
\item $E$ is the $\RealUp$ seal row reached only after the finite windows and regular-rational readbacks have been displayed.
\item $X$ is the source $\MetricUp$ row, including the local source-radius requests consumed by the continuity rows in $F$.
\item $Y$ is the target $\MetricUp$ row, including the target tolerance ledger consumed by $L,R,E$.
\item $H$ records componentwise $\hsame$ transport for $F,L,W,R,E,X,Y,C,P,N$.
\item $C$ records displayed $\Cont$ replay from a limit-continuity request through $X,Y,F,L,W,R,E$ and then through the structural rows.
\item $P$ is the $\Pkg$ provenance over $\UniformLimitTheoremUp$, $\ContinuousMapUp$, $\UniformLimitUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\MetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformLimitTheoremUp}$ row.
\end{enumerate}
The carrier has no coordinate for an ambient topology on maps, a host-level selected limit function, quotient stream equality, countable choice, or completeness of the target metric space beyond the displayed rows.
\end{definition}

\begin{theorem}[Uniform-limit theorem NameCert obligations]
\label{thm:uniform-limit-theorem-namecert-obligations}
For an accepted $\UniformLimitTheoremUp$ carrier $U=(F,L,W,R,E,X,Y,H,C,P,N)$, the local $\NameCert_{\UniformLimitTheoremUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed tuple over the $\ContinuousMapUp$ sequence, $\UniformLimitUp$ ledger, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\RealUp$ seals, and source and target $\MetricUp$ rows;
\item uniform-limit visibility, requiring every limit-continuity read to pass through the modulus ledger $L$ before any window or real-seal row is exposed;
\item continuity inheritance, requiring the source-radius row read from a member of $F$ and the tail bound read from $L$ to be jointly visible before the limit row is named continuous;
\item finite-window discipline, requiring every sequence value and limit candidate used by the handoff to be read through $W$ and then through $R$;
\item $\RealUp$-seal nonescape, requiring the terminal real seal $E$ to appear only after $L,W,R$ and the target metric row $Y$ have been displayed;
\item transport and replay stability through the componentwise $\hsame$ row $H$ and displayed $\Cont$ row $C$;
\item provenance exhaustion through $P$ and the local naming row $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-limit-theorem-carrier}. It exposes the continuous-map sequence, the uniform-limit ledger, finite windows, regular readbacks, real seals, metric rows, transport, replay, provenance, and local naming rows.

Uniform-limit visibility is the role of $L$. A target tolerance first selects a displayed tail stage and the source-radius information needed for the limit read. Only then may the route inspect the finite windows $W$ and regular readbacks $R$.

Continuity inheritance uses $F$ together with $L$. The chosen member of the continuous sequence supplies the local source-radius row, while the uniform-limit ledger supplies the tail comparison that transfers the target tolerance to the limit candidate.

The Real-facing end of the route is $W,R,E$. The windows expose only finite observations, the readback row repacks those observations as regular rational data, and the $\RealUp$ seal appears after these rows and the target metric row have been displayed.

Finally $H,C,P,N$ transport, replay, package, and name the same route. Since the carrier lacks ambient map topology, quotient stream equality, selected host limits, choice, and target-completeness coordinates, no further obligation can be read from the local certificate.
\end{proof}

\begin{theorem}[Uniform limit preserves continuity as a BEDC handoff]
\label{thm:uniform-limit-theorem-continuous-handoff}
Every continuity read of the limit named by an accepted $\UniformLimitTheoremUp$ carrier factors through the displayed route
$$
X,Y \longmapsto F,L \longmapsto W,R \longmapsto E,H,C,P,N .
$$
Thus the source and target $\MetricUp$ rows are read first, the $\ContinuousMapUp$ sequence and $\UniformLimitUp$ ledger supply the continuity and tail witnesses, the $\StreamNameUp$ and $\RegSeqRatUp$ rows expose only finite readbacks, and the $\RealUp$ seal is reached only at the end of the route. No consumer of the packet receives an ambient function-space topology, a selected host limit, quotient stream equality, countable choice, or target completeness not present in the carrier.
\end{theorem}
\begin{proof}
Begin with a continuity request for the limit. The only source and target data available are the metric rows $X$ and $Y$, so the request first reads the source-radius and target-tolerance surfaces recorded there.

Next the route reads $F$ and $L$. The sequence row $F$ provides the continuous-map witness at the displayed tail stage, while $L$ provides the uniform-limit budget that lets the same target tolerance be compared with the limit candidate.

The finite observation stage is $W,R$. The selected sequence value and the limit candidate are exposed through StreamName windows and then through RegSeqRat readbacks; no quotient stream or host function value is available.

The terminal stage is $E,H,C,P,N$. The Real seal is reached only after the finite readbacks have been fixed, and the structural rows transport, replay, package, and name the same finite route. This proves that continuity of the limit is a BEDC handoff through the displayed uniform-limit ledger rather than an appeal to an ambient theorem outside the packet.
\end{proof}

\closureat{UniformLimitTheoremUp}{seedStr}

\begin{closurestatus}{\UniformLimitTheoremUp}
  \constructivestory{A $\UniformLimitTheoremUp$ packet is generated from a ContinuousMapUp sequence ledger, a UniformLimitUp modulus ledger, finite StreamNameUp windows, RegSeqRatUp readbacks, RealUp seals, source and target MetricUp rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-limit-theorem-carrier}, \autoref{thm:uniform-limit-theorem-namecert-obligations}, and \autoref{thm:uniform-limit-theorem-continuous-handoff} seed the finite theorem handoff from ContinuousMapUp and UniformLimitUp rows through StreamNameUp, RegSeqRatUp, RealUp, and MetricUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, ambient function-space topology, quotient stream equality, selected host limits, countable choice, or target completeness beyond the displayed rows.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform-limit visibility, continuity inheritance, finite-window discipline, Real-seal nonescape, transport and replay stability, and provenance exhaustion for BEDC.Derived.UniformLimitTheoremUp.}
\end{closurestatus}
