\chapter{A Concrete Naming Certificate for $\RealPrefixDiagnosticUp$}
\label{ch:concrete-instances-real-prefix-diagnostic-namecert}
\origin{human}

Following Bishop--Bridges regular Cauchy real names and the finite-readback route of \autoref{ch:visions-real-completeness}, the $\RealPrefixDiagnosticUp$ packet records the prefix-window diagnostic surface used before a $\RealUp$ seal is read. It sits after the finite cylinder interface of \autoref{ch:concrete-instances-real-baire-cylinder-namecert}, the observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational source rows of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite diagnostic object for the Real-completeness route; it is not a proof of $\RealUp$ completeness, a quotient of Cauchy names, a selected host limit, countable choice, trichotomy, or host real equality.

\begin{definition}[Real prefix-diagnostic carrier]
\label{def:real-prefix-diagnostic-carrier}
A $\RealPrefixDiagnosticUp$ carrier is a finite $\BHist$ packet
$$
Q=(B,W,S,R,D,E,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\RealBaireCylinderUp$ prefix-cylinder row naming the finite branch of the real-name read.
\item $W$ is the prefix-window budget row, recording the bounded observation depth and the precision request that opened the diagnostic.
\item $S$ is the $\StreamNameUp$ row inspected inside the same finite window.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the inspected StreamName entries.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row comparing the requested precision with the regular rational readback.
\item $E$ is the terminal $\RealUp$ seal row, available only after $B,W,S,R,D$ have been replayed.
\item $A$ is the diagnostic answer row. It records pass, refine-window, or reject-at-prefix outcomes as finite rows rather than as host real decisions.
\item $H$ records componentwise $\hsame$ transport for prefix cylinders, window budgets, StreamName rows, RegSeqRat readbacks, dyadic tolerances, Real seals, diagnostic answers, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
B,W \longmapsto S \longmapsto R \longmapsto D \longmapsto E,A,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\RealPrefixDiagnosticUp$, $\RealBaireCylinderUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealPrefixDiagnosticUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $B,W,S,R,D,E,A,H,C,P,N$. The carrier has no coordinate for a completed real object, quotient Cauchy equality, selected limits, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Real prefix-diagnostic NameCert obligations]
\label{thm:real-prefix-diagnostic-namecert-obligations}
For every accepted $\RealPrefixDiagnosticUp$ carrier
$$
Q=(B,W,S,R,D,E,A,H,C,P,N),
$$
the local $\NameCert_{\RealPrefixDiagnosticUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the RealBaireCylinder prefix, prefix-window budget, StreamName observations, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, diagnostic answer, transport, replay, provenance, and local naming rows;
\item prefix-window exactness, requiring every diagnostic request to read $B$ and $W$ before any StreamName entry is inspected;
\item regular readback discipline, requiring each inspected window to pass through $S$ and $R$ before the dyadic tolerance row $D$ compares the requested precision;
\item Real-seal boundary, requiring the $\RealUp$ row $E$ to be read only after the finite prefix, stream, regular-rational, and dyadic rows have been displayed;
\item diagnostic-answer confinement, requiring $A$ to report only finite pass, refine-window, or reject-at-prefix rows and no host real decision;
\item transport, replay, and provenance exhaustion through $H,C,P,N$.
\end{enumerate}
No RealPrefixDiagnostic obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:real-prefix-diagnostic-carrier}. The tuple displays the prefix cylinder, finite window budget, StreamName observations, RegSeqRat readback, dyadic tolerance, Real seal, diagnostic answer, and structural rows.

The prefix-window obligation reads $B$ and $W$ first. These rows bind the finite branch and depth of the diagnostic, so no later row can inspect an unbounded stream or a host real representative.

The regular readback obligation is the route through $S,R,D$. StreamName entries are inspected only within the displayed window, the regular rational row repacks that finite observation, and the dyadic row compares it with the requested tolerance.

The Real-seal boundary is row $E$, and the diagnostic answer is row $A$. The answer can report finite success, a request for a deeper window, or rejection at the displayed prefix, but it cannot decide equality of host reals or select a completed limit.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier has no completed-real, quotient, selected-limit, choice, trichotomy, host-equality, verification, or bridge coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real prefix-diagnostic Real-seal readback]
\label{thm:real-prefix-diagnostic-real-seal-readback}
Every Real-completeness route consumer of an accepted $\RealPrefixDiagnosticUp$ packet factors its finite diagnostic read through
$$
B,W \longmapsto S \longmapsto R \longmapsto D \longmapsto E,A,H,C,P,N .
$$
Thus prefix-cylinder data are inspected before StreamName rows, StreamName rows before RegSeqRat readback, RegSeqRat rows before dyadic tolerance comparison, and the $\RealUp$ seal only after those finite rows are displayed. The packet exports no completed $\RealUp$ proof, quotient Cauchy class, selected host limit, countable-choice schedule, trichotomy, or host real equality.
\end{theorem}
\begin{proof}
Begin with a finite diagnostic read for the Real-completeness route. The only prefix data exposed by the carrier are $B$ and $W$, so the consumer first fixes the displayed cylinder and bounded observation depth.

The stream and rational readback stages then follow. The row $S$ exposes only the StreamName entries inside that window, while $R$ repacks those entries as regular rational readback data.

The tolerance check is row $D$. It compares the requested precision with the displayed readback before the Real seal is available.

Only then can the route read $E$ and the diagnostic answer $A$. Transport through $H$, replay through $C$, and provenance through $P,N$ preserve this order, so the consumer receives a finite prefix diagnostic rather than a completed-real or choice-based object.
\end{proof}

\closureat{RealPrefixDiagnosticUp}{seedStr}

\begin{closurestatus}{\RealPrefixDiagnosticUp}
  \constructivestory{A $\RealPrefixDiagnosticUp$ packet is generated from a RealBaireCylinder prefix row, finite prefix-window budget, StreamName row, RegSeqRat readback, DyadicRatCore tolerance row, RealUp seal row, diagnostic answer row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-prefix-diagnostic-carrier}, \autoref{thm:real-prefix-diagnostic-namecert-obligations}, and \autoref{thm:real-prefix-diagnostic-real-seal-readback} seed the finite prefix-window diagnostic route before a RealUp seal is read.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close RealUp completeness, quotient Cauchy equality, selected limits, countable choice, trichotomy, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, prefix-window exactness, regular readback discipline, dyadic tolerance comparison, Real-seal boundary, diagnostic-answer confinement, transport, replay, provenance, and local naming for BEDC.Derived.RealPrefixDiagnosticUp.}
\end{closurestatus}
