\chapter{A Concrete Naming Certificate for $\HausdorffCompletionUniversalUp$}
\label{ch:concrete-instances-hausdorff-completion-universal-namecert}
\origin{human}

Following Bourbaki and Kelley on metric completion and separated uniform spaces, the $\HausdorffCompletionUniversalUp$ packet records the separated universal-property surface for completion. It sits between the metric completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the separated metric boundary of \autoref{ch:concrete-instances-separatedmetric-namecert}, the uniform completion route of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the extension-and-uniqueness packet of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, and the quotient-free separated reflection boundary of \autoref{ch:concrete-instances-hausdorff-reflection-namecert}. The packet names the finite handoff by which dense source data extend into a separated target without importing quotient completion, representative choice, host equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[HausdorffCompletionUniversal carrier]
\label{def:hausdorff-completion-universal-carrier}
A $\HausdorffCompletionUniversalUp$ carrier is a finite $\BHist$ packet
$$
U=(M,Q,S,D,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source $\MetricCompletionUp$ row. It records the metric source, completion-facing seal, and finite request boundary consumed by the universal-property route.
\item $Q$ is the completion seal row. It records the completed object as a displayed seal, not as a host quotient of Cauchy names.
\item $S$ is the separated target row. It records the $\SeparatedMetricUp$ or Hausdorff-facing target exactness consumed by uniqueness.
\item $D$ is the dense-source handoff row. It records the source inclusion and dense read through which maps out of the source are inspected.
\item $E$ is the extension row. It records the finite $\Cont$ route that extends the dense-source map into the separated target.
\item $L$ is the uniqueness row. It records the displayed separatedness comparison showing that two extensions with the same dense-source reads are $\hsame$-identified.
\item $H$ records componentwise $\hsame$ transport for the source metric, completion seal, separated target, dense handoff, extension, uniqueness, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
M,Q,D \longmapsto S,E,L \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\HausdorffCompletionUniversalUp$, $\MetricCompletionUp$, $\SeparatedMetricUp$, $\UniformCompletionUp$, $\CompletionUniversalPropertyUp$, $\HausdorffReflectionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HausdorffCompletionUniversalUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,Q,S,D,E,L,H,C,P,N$. It has no coordinate for quotient completion, selected representatives, host equality of completed points, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[HausdorffCompletionUniversal NameCert obligations]
\label{thm:hausdorff-completion-universal-namecert-obligations}
For an accepted $\HausdorffCompletionUniversalUp$ carrier $U=(M,Q,S,D,E,L,H,C,P,N)$, the local $\NameCert_{\HausdorffCompletionUniversalUp}$ surface consists exactly of carrier admission; separated target exactness through $S$; dense-source handoff through $D$; extension existence through $E$; uniqueness through the separatedness ledger $L$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $C$; provenance and local naming through $P,N$; and non-escape from quotient completion, representative choice, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:hausdorff-completion-universal-carrier}. The accepted packet exposes exactly the metric-completion source, completion seal, separated target, dense handoff, extension, uniqueness, transport, replay, provenance, and local naming rows.

Separated target exactness is the row $S$. A uniqueness read cannot inspect host equality of completed points; it can only read the separated target row and the displayed comparison ledger carried by $L$.

The extension surface is finite. The dense-source handoff $D$ supplies the source reads, and the extension row $E$ repacks those reads through a displayed $\Cont$ route into the separated target.

Transport and replay preserve the same packet. Rows $H$ and $C$ move only the displayed coordinates $M,Q,S,D,E,L,P,N$, while $P$ and $N$ record provenance and local naming for that route. Since no excluded host-side coordinate exists in the carrier, the listed rows exhaust the local $\NameCert$ surface.
\end{proof}

\falsifiablePrediction{Every accepted $\HausdorffCompletionUniversalUp$ consumer reads a MetricCompletion source row, a completion seal row, a SeparatedMetric target row, a dense-source handoff row, an extension row, a uniqueness row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before citing the separated universal property.}

\independenceWitness{metriccompletion, separatedmetric, uniformcompletion, completionuniversalproperty, hausdorffreflection: $\HausdorffCompletionUniversalUp$ is not bijective to any listed sibling because it jointly carries a completion seal, separated target exactness, dense-source handoff, extension, uniqueness, transport, replay, provenance, and local naming as one finite universal-property packet.}

\closureat{HausdorffCompletionUniversalUp}{seedStr}

\begin{closurestatus}{\HausdorffCompletionUniversalUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-completion-universal-carrier} and \autoref{thm:hausdorff-completion-universal-namecert-obligations} seed the separated universal-property surface for completion over $\MetricCompletionUp$, $\SeparatedMetricUp$, $\UniformCompletionUp$, $\CompletionUniversalPropertyUp$, $\HausdorffReflectionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, host equality of completed points, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, separated target exactness, dense-source handoff, extension existence, uniqueness through separatedness, transport and replay stability, provenance non-escape, and TasteGate field faithfulness for BEDC.Derived.HausdorffCompletionUniversalUp.}
  \constructivestory{A $\HausdorffCompletionUniversalUp$ packet is generated from a MetricCompletion source row, completion seal, separated target row, dense-source handoff, extension row, uniqueness row, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
\end{closurestatus}
