\chapter{A Concrete Naming Certificate for $\FiniteObservationConfluenceUp$}
\label{ch:concrete-instances-finite-observation-confluence-namecert}
\origin{ai}

The $\FiniteObservationConfluenceUp$ packet realizes the typed-example audit surface of \autoref{ch:metacic-typedexamples-audit-map} as finite confluence-facing observation data. It sits between the typed examples gallery of \autoref{ch:concrete-instances-typedexamplegallery-namecert}, the coverage matrix of \autoref{ch:concrete-instances-typedexamplecoveragematrix-namecert}, the finite observation-budget selector of \autoref{ch:concrete-instances-finiteobservationbudgetselector-namecert}, the bounded normal equality checker of \autoref{ch:concrete-instances-bounded-normal-equality-checker-namecert}, and the confluence critical-pair boundary of \autoref{ch:concrete-instances-metacic-confluence-critical-pair-boundary-namecert}. The packet records selected typed examples, reduction observations, normal-form comparisons, and a critical-pair boundary handoff; it is not a theorem of global confluence.

\falsifiablePrediction{Every accepted $\FiniteObservationConfluenceUp$ audit read exposes typed-example rows, finite observation-budget rows, reduction observations, bounded normal-equality rows, confluence-boundary handoff rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming before it can be cited by a confluence audit consumer.}

\independenceWitness{typedexamplegallery, typedexamplecoveragematrix, finiteobservationbudgetselector, boundednormalequalitychecker, metacic-confluence-critical-pair-boundary: $\FiniteObservationConfluenceUp$ is not bijective to any listed sibling because it jointly carries typed-example selection, finite budget, reduction observation, normal comparison, confluence-boundary handoff, transport, replay, provenance, and local naming rows.}

\begin{definition}[FiniteObservationConfluence carrier]
\label{def:finite-observation-confluence-carrier}
A $\FiniteObservationConfluenceUp$ carrier is a finite $\BHist$ packet
$$
F=(T,B,R,E,Q,J,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the typed-example row read from the MetaCIC gallery and coverage-matrix surface.
\item $B$ is the $\FiniteObservationBudgetSelectorUp$ row bounding which example observations are admitted.
\item $R$ is the reduction-observation row, recording the displayed beta, application, projection, or eliminator computation inspected by the packet.
\item $E$ is the $\BoundedNormalEqualityCheckerUp$ row used when the observation is compared by bounded normal equality.
\item $Q$ is the $\MetaCICConfluenceCriticalPairBoundaryUp$ handoff row, recording the critical-pair and common-reduct boundary available to the same observation.
\item $J$ is the confluence-observation ledger row tying the typed example, budget, reduction observation, bounded checker, and critical-pair boundary to one finite audit route.
\item $H$ records componentwise $\hsame$ transport for the typed-example, budget, reduction, bounded-checker, boundary, ledger, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the typed example through $T,B,R,E,Q,J,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteObservationConfluenceUp$, $\FiniteObservationBudgetSelectorUp$, $\MetaCICConfluenceCriticalPairBoundaryUp$, $\BoundedNormalEqualityCheckerUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteObservationConfluenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,B,R,E,Q,J,H,C,P,N$. It has no coordinate for arbitrary closed-term Church--Rosser, full parallel diamond, strong normalisation, subject reduction, residual-substitution compatibility, or unchecked conversion decidability.
\end{definition}

\begin{theorem}[FiniteObservationConfluence NameCert obligations]
\label{thm:finite-observation-confluence-namecert-obligations}
For every accepted $\FiniteObservationConfluenceUp$ carrier $F=(T,B,R,E,Q,J,H,C,P,N)$, the local $\NameCert_{\FiniteObservationConfluenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the typed-example row, finite observation budget, reduction observation, bounded equality checker, confluence-boundary handoff, observation ledger, transport, replay, provenance, and local naming row;
\item typed-example exactness, requiring $T$ to name an accepted gallery or coverage-matrix example before any reduction observation is read;
\item budget accountability, requiring $B$ to bound the visible observation route for the selected example;
\item reduction-observation exactness, requiring $R$ to display the beta, application, projection, or eliminator computation actually inspected by the packet;
\item bounded-comparison handoff, requiring $E$ to consume only the displayed observation rows;
\item confluence-boundary handoff, requiring $Q$ to read only the finite critical-pair and common-reduct boundary available to the same observation;
\item ledger non-escape, requiring $J,H,C,P,N$ to transport, replay, source, and name the same finite route without exporting global confluence, subject reduction, strong normalisation, residual-substitution compatibility, or unchecked conversion decidability.
\end{enumerate}
No FiniteObservationConfluence obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:finite-observation-confluence-carrier}. The projection exposes exactly $T,B,R,E,Q,J,H,C,P,N$.

The typed-example and budget rows are read first. The row $T$ names the gallery example, and $B$ restricts the observation route to a finite budget.

The reduction observation is then displayed by $R$. The bounded checker $E$ may compare only the rows already exposed by the typed-example, budget, and reduction observation.

The confluence-boundary handoff $Q$ is similarly downstream of the finite observation. It may read the critical-pair and common-reduct boundary, but it does not turn the packet into a global confluence theorem.

Finally $J,H,C,P,N$ ledger, transport, replay, source, and name the same route. Since the excluded metatheorems are not coordinates of the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[FiniteObservationConfluence MetaCIC handoff]
\label{thm:finite-observation-confluence-metacic-handoff}
Let $F=(T,B,R,E,Q,J,H,C,P,N)$ be an accepted $\FiniteObservationConfluenceUp$ carrier. Every MetaCIC confluence-audit consumer of $F$ factors through the displayed route
$$
T \longmapsto B \longmapsto R \longmapsto E \longmapsto Q \longmapsto J \longmapsto H,C,P,N .
$$
Consequently typed-example checker rows, reduction observations, and confluence-boundary handoff are consumed as one finite observation packet, not as a claim of arbitrary confluence.
\end{theorem}
\begin{proof}
Start with a confluence-audit consumer of $F$. The carrier gives no direct coordinate for arbitrary Church--Rosser, full parallel diamond, subject reduction, strong normalisation, or residual-substitution compatibility.

The consumer must first read the typed-example row $T$ and the finite budget row $B$. These rows identify the concrete example and the finite observation surface.

The reduction row $R$ and bounded checker row $E$ then supply the inspected computation and comparison data. They are tied to the same budget and cannot range over arbitrary closed terms.

The critical-pair boundary row $Q$ is read only after the finite observation is displayed. The ledger and structural rows $J,H,C,P,N$ then record, transport, replay, source, and name the same route, proving the stated factorization.
\end{proof}

The Lean TasteGate surface for this packet must provide \texttt{Nontrivial FiniteObservationConfluenceUp} and \texttt{FieldFaithful FiniteObservationConfluenceUp}. The field-faithfulness check must keep the typed-example row, finite budget row, reduction-observation row, bounded-checker row, confluence-boundary handoff row, and ledger row as distinct carrier fields rather than aliases for a global confluence theorem.

\closureat{FiniteObservationConfluenceUp}{seedStr}

\begin{closurestatus}{\FiniteObservationConfluenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-observation-confluence-carrier}, \autoref{thm:finite-observation-confluence-namecert-obligations}, and \autoref{thm:finite-observation-confluence-metacic-handoff} seed the finite typed-example observation route from checker rows and reduction observations to confluence-boundary handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close arbitrary closed-term Church--Rosser, full parallel diamond, subject reduction, strong normalisation, residual-substitution compatibility, unchecked conversion decidability, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, typed-example exactness, budget accountability, reduction-observation exactness, bounded-comparison handoff, confluence-boundary handoff, ledger non-escape, and TasteGate nontriviality and field faithfulness for BEDC.Derived.FiniteObservationConfluenceUp.}
  \constructivestory{A $\FiniteObservationConfluenceUp$ packet is generated from typed-example rows, a finite observation-budget selector row, reduction-observation rows, a bounded normal-equality checker row, a MetaCIC confluence critical-pair boundary handoff, a confluence-observation ledger, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
