\chapter{A Concrete Naming Certificate for $\UniformContinuityModulusUp$}
\label{ch:concrete-instances-uniform-continuity-modulus-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\UniformContinuityModulusUp$ packet records the explicit tolerance-to-radius surface used by uniformly continuous maps between metric carriers. It sits between the source and target metric certificates of \autoref{ch:concrete-instances-metric-namecert}, the pointwise continuous-map interface of \autoref{ch:concrete-instances-continuousmap-namecert}, the consumer modulus surface of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the compact finite-net production route of \autoref{ch:concrete-instances-heine-cantor-modulus-namecert}. Its role is to expose a named finite carrier for continuity moduli, not to assert open-cover compactness, selected real representatives, quotient equality of functions, or ambient completeness.

\begin{definition}[Uniform continuity modulus carrier]
\label{def:uniform-continuity-modulus-carrier}
A $\UniformContinuityModulusUp$ carrier is a finite $\BHist$ packet
$$
U=(X,Y,F,\varepsilon,\delta,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source $\MetricUp$ row, including the displayed source-distance classifier and the source-side tolerance comparison used by the modulus.
\item $Y$ is the target $\MetricUp$ row, including the displayed target-distance classifier and the target triangle ledger consumed by later estimates.
\item $F$ is the $\ContinuousMapUp$ row whose graph and pointwise-continuity reads are constrained by the same source and target metric rows.
\item $\varepsilon$ is the positive target tolerance history requested by the consumer.
\item $\delta$ is the positive source radius history selected for that target tolerance.
\item $M$ is the $\UniformModulusUp$ consumer row receiving the displayed implication from source closeness below $\delta$ to target closeness below $\varepsilon$.
\item $H$ records componentwise $\hsame$ transport for $X,Y,F,\varepsilon,\delta,M$ and for the local classifier row.
\item $C$ records the displayed $\Cont$ replay routes by which a consumer reads the same source metric, target metric, continuous-map, tolerance, radius, and modulus rows.
\item $P$ is the $\Pkg$ provenance over $\UniformContinuityModulusUp$, $\MetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformContinuityModulusUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by replaying $X,Y,F,\varepsilon,\delta,M,H,C,P,N$. It has no coordinate for a compactness theorem, selected finite net, open-cover argument, quotient function equality, host function extensionality, or ambient completion principle.
\end{definition}

\begin{theorem}[Uniform continuity modulus NameCert obligations]
\label{thm:uniform-continuity-modulus-namecert-obligations}
For every accepted $\UniformContinuityModulusUp$ carrier $U=(X,Y,F,\varepsilon,\delta,M,H,C,P,N)$, the local $\NameCert_{\UniformContinuityModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source metric, target metric, continuous-map row, target tolerance, source radius, uniform-modulus handoff, transport, replay, provenance, and local name;
\item tolerance-radius exactness, requiring $\varepsilon$ and $\delta$ to be read before the $\UniformModulusUp$ consumer row $M$ is available;
\item continuous-map accountability, requiring every function read to pass through the displayed $\ContinuousMapUp$ row $F$ and the source and target metric rows $X,Y$;
\item componentwise transport and replay stability under $H$ and $C$ for the same finite rows;
\item ledger refusal, stating that compactness, selected finite nets, open covers, quotient function equality, host extensionality, and completion data are not carrier coordinates.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:uniform-continuity-modulus-carrier}. It exposes exactly the source and target metrics, continuous-map row, tolerance, radius, uniform-modulus handoff, and structural rows.

The target tolerance and source radius are read before the consumer row. Thus the $\UniformModulusUp$ handoff can inspect only the displayed implication from source closeness below $\delta$ to target closeness below $\varepsilon$.

The row $F$ supplies the continuous-map boundary, while $H,C,P,N$ transport, replay, source, and name the same packet. Since compactness, finite-net selection, open covers, quotient equality, host extensionality, and completion data are absent from the carrier, no NameCert obligation can export them.
\end{proof}

\begin{theorem}[ContinuousMap handoff]
\label{thm:uniform-continuity-modulus-continuousmap-handoff}
Every $\ContinuousMapUp$ consumer of an accepted $\UniformContinuityModulusUp$ carrier factors through the displayed route
$$
X,Y,F,\varepsilon,\delta \longmapsto M \longmapsto H,C,P,N .
$$
The consumer receives the source metric row, target metric row, continuous-map row, requested target tolerance, selected source radius, uniform-modulus handoff, transport, replay, provenance, and local naming. It receives no full host function, compactness theorem, open-cover proof, quotient equality of functions, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with a $\ContinuousMapUp$ read of the packet. By \autoref{def:uniform-continuity-modulus-carrier}, the only function-facing coordinate is $F$, and it is stored beside the metric rows $X,Y$ and the tolerance-radius pair $\varepsilon,\delta$.

The consumer handoff is the row $M$. It can be reached only after the tolerance and radius rows have been displayed, and the rows $H,C,P,N$ keep the same route under transport, replay, provenance, and local naming.

Therefore every continuous-map consumer sees a finite modulus boundary over the displayed metric and continuous-map rows. The excluded host function, compactness, open-cover, quotient-equality, and completeness objects have no coordinate in the accepted packet.
\end{proof}

\begin{theorem}[Composition stability]
\label{thm:uniform-continuity-modulus-composition-stability}
Let $U_1=(X,Y,F,\varepsilon_1,\delta_1,M_1,H_1,C_1,P_1,N_1)$ and $U_2=(Y,Z,G,\varepsilon_2,\delta_2,M_2,H_2,C_2,P_2,N_2)$ be accepted $\UniformContinuityModulusUp$ carriers with the target metric row of $U_1$ matching the source metric row of $U_2$ under the displayed $\hsame$ transport. A composed consumer may form its public modulus only by reading the outer target tolerance in $U_2$, the source radius selected by $U_2$ as a target tolerance for $U_1$, the source radius selected by $U_1$, and the two displayed $\UniformModulusUp$ handoff rows. The composed route exports no hidden compactness selector, host function composition theorem, quotient-map equality, or completeness witness.
\end{theorem}
\begin{proof}
Read the second carrier first. Its target tolerance $\varepsilon_2$ selects the source radius $\delta_2$ through $M_2$, and the shared metric row identifies $\delta_2$ as the tolerance request consumed by the first carrier.

Read the first carrier at that displayed tolerance. Its source radius $\delta_1$ and handoff row $M_1$ provide the source-side control needed before the outer handoff $M_2$ is applied.

The componentwise transports $H_1,H_2$ and replay rows $C_1,C_2$ keep both packets on the same displayed metric boundary. Since neither packet contains compactness, host function composition, quotient equality, or completeness data, the composed consumer cannot export any of those objects.
\end{proof}

\falsifiablePrediction{Every $\UniformContinuityModulusUp$ consumer factors through source and target MetricUp rows, a ContinuousMapUp row, a positive target tolerance, a positive source radius, a UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{continuousmap, uniformmodulus, heinecantormodulus, metric: $\UniformContinuityModulusUp$ is not bijective to any listed sibling because it jointly carries the source metric, target metric, ContinuousMap row, target tolerance, source radius, UniformModulus consumer handoff, transport, replay, provenance, and local NameCert rows as one finite modulus packet.}

\closureat{UniformContinuityModulusUp}{seedStr}

\begin{closurestatus}{\UniformContinuityModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-continuity-modulus-carrier}, \autoref{thm:uniform-continuity-modulus-namecert-obligations}, \autoref{thm:uniform-continuity-modulus-continuousmap-handoff}, and \autoref{thm:uniform-continuity-modulus-composition-stability} seed the finite explicit-modulus surface over source metric, target metric, ContinuousMap, tolerance-radius, and UniformModulus consumer rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close compactness, open-cover arguments, selected finite nets, quotient function equality, host function extensionality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tolerance-radius exactness, ContinuousMap handoff, composition stability, and field faithfulness for BEDC.Derived.UniformContinuityModulusUp.}
  \constructivestory{A $\UniformContinuityModulusUp$ packet is generated from a source MetricUp row, a target MetricUp row, a ContinuousMap row, a positive target tolerance, a positive source radius, a UniformModulus consumer row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
