\chapter{A Concrete Naming Certificate for $\CodonSixBitWindowUp$}
\label{ch:concrete-instances-codon-six-bit-window-namecert}
\origin{ai}

The $\CodonSixBitWindowUp$ packet realizes the codon source atlas of \autoref{subsec:philosophy-codon-window-six-bridge} as finite BEDC NameCert data. It reads each base through a two-coordinate $\BoolUp$ atlas, packages the three base positions through the product and list surfaces of \autoref{ch:concrete-instances-prod-namecert} and \autoref{ch:concrete-instances-list-namecert}, compares no-$11$ suffix constraints against \autoref{ch:concrete-instances-fibonaccicube-namecert}, and hands the stop-face suffix row to \autoref{ch:concrete-instances-stopcodonzeckendorfsuffix-namecert}. The packet records the six-coordinate source window and Flat6 readback; it does not identify source-space equality with the biological translation classifier.

\begin{definition}[Codon six-bit window carrier]
\label{def:codon-six-bit-window-carrier}
A $\CodonSixBitWindowUp$ carrier is a finite $\BHist$ packet
$$
W=(B,A,L,F,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BoolUp$ coordinate row. It records the two binary axes used to read each base in the codon source atlas.
\item $A$ is the three-position atlas row. It records the first, second, and third base windows as ordered pairs of Bool coordinates.
\item $L$ is the $\ListUp$ spine row. It records the ordered six-coordinate window and preserves position order for downstream reads.
\item $F$ is the Flat6 readback row. It flattens the three two-coordinate base rows into one six-coordinate source-space vector.
\item $S$ is the suffix-handoff row. It records the comparison with $\FibonacciCubeUp$ no-$11$ suffix discipline and the handoff to $\StopCodonZeckendorfSuffixUp$ for stop-face reads.
\item $H$ records componentwise $\hsame$ transport for Bool coordinates, product pairs, list spine, Flat6 readback, suffix handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
B,A,L \longmapsto F,S \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CodonSixBitWindowUp$, $\BoolUp$, $\ProdUp$, $\ListUp$, $\FibonacciCubeUp$, $\StopCodonZeckendorfSuffixUp$, the codon-window-six bridge, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CodonSixBitWindowUp}$ row.
\end{enumerate}
The classifier compares packets through $B,A,L,F,S,H,C,P,N$. It has no coordinate for biological translation-table identity, amino-acid classification, stochastic codon usage, quotient codon equality, or a selected global code table.
\end{definition}

\begin{theorem}[Codon six-bit window NameCert obligations]
\label{thm:codon-six-bit-window-namecert-obligations}
For an accepted $\CodonSixBitWindowUp$ carrier $W=(B,A,L,F,S,H,C,P,N)$, the local $\NameCert_{\CodonSixBitWindowUp}$ surface consists exactly of carrier admission, Bool-coordinate exactness, three-position atlas order, List spine preservation, Flat6 readback exactness, Fibonacci-cube suffix comparison, StopCodonZeckendorfSuffix handoff, transport and replay stability, provenance, local naming, and non-escape of biological translation-table identity or amino-acid classification.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:codon-six-bit-window-carrier}. The Bool-coordinate row $B$ and three-position atlas row $A$ expose exactly six source coordinates, grouped as three ordered base windows.

The list spine row $L$ keeps the six coordinates ordered, and the Flat6 row $F$ is the only readback that forgets the three-pair grouping while preserving the same source-space coordinates.

The suffix row $S$ compares the final two-coordinate suffix with the finite no-$11$ discipline of \autoref{ch:concrete-instances-fibonaccicube-namecert} and the stop-face handoff of \autoref{ch:concrete-instances-stopcodonzeckendorfsuffix-namecert}. This is a source-window handoff, not a biological translation classifier.

The rows $H,C,P,N$ transport, replay, source, and locally name the same route. Since no translation-table or amino-acid row exists in the carrier, those classifiers cannot be exported by the accepted packet.
\end{proof}

\begin{theorem}[Codon six-bit Flat6 readback]
\label{thm:codon-six-bit-window-flat-six-readback}
Every accepted $\CodonSixBitWindowUp$ source-space read factors through
$$
B,A,L \longmapsto F
$$
before it can reach the suffix-handoff row $S$ or the structural rows $H,C,P,N$. Thus Flat6 equality is equality of the displayed six-coordinate source window, not equality of biological translation classifiers.
\end{theorem}
\begin{proof}
Read $B$ to obtain the Bool coordinate axes and $A$ to group them into three base positions. The product surface preserves the two-coordinate base rows before any flattening occurs.

Read $L$ to preserve the ordered six-coordinate spine. The Flat6 row $F$ is then the unique route that exposes the same coordinates as one source-space vector.

Only after $F$ is displayed may a consumer inspect the suffix handoff $S$ or the structural rows $H,C,P,N$. Therefore any packet identifying Flat6 source-space equality with biological translation classification leaves the accepted carrier surface.
\end{proof}

\falsifiablePrediction{Any $\CodonSixBitWindowUp$ packet that identifies Flat6 source-space equality with the biological translation classifier fails the classifier row, because the accepted carrier has only Bool-coordinate, product/list spine, Flat6 readback, suffix-handoff, transport, replay, provenance, and local naming rows.}

\independenceWitness{stopcodonzeckendorfsuffix, codon\_window\_spectral\_inverse, fibonaccicube, bool, list: $\CodonSixBitWindowUp$ is not bijective to any listed sibling because the explicit six-coordinate Flat6 row and suffix-handoff row jointly preserve source-window equality while refusing biological translation-classifier identity.}

The Lean TasteGate follow-up is \texttt{BEDC.Derived.CodonSixBitWindowUp.TasteGate}, with explicit $\Nontrivial\ \CodonSixBitWindowUp$ and $\FieldFaithful\ \CodonSixBitWindowUp$ instances preserving $B,A,L,F,S,H,C,P,N$ as separate displayed fields.

\closureat{CodonSixBitWindowUp}{seedStr}

\begin{closurestatus}{\CodonSixBitWindowUp}
  \constructivestory{A $\CodonSixBitWindowUp$ packet is generated from BoolUp coordinate rows, a three-position product atlas, an ordered ListUp spine, Flat6 readback, FibonacciCubeUp suffix comparison, StopCodonZeckendorfSuffixUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:codon-six-bit-window-carrier}, \autoref{thm:codon-six-bit-window-namecert-obligations}, and \autoref{thm:codon-six-bit-window-flat-six-readback} seed the finite six-coordinate source-window packet and its Flat6 readback boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological translation-table identity, amino-acid classification, stochastic codon usage, quotient codon equality, selected global code tables, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Bool-coordinate exactness, product/list spine preservation, Flat6 readback, suffix handoff, nontriviality, and field faithfulness for BEDC.Derived.CodonSixBitWindowUp.TasteGate.}
\end{closurestatus}
