\chapter{A Concrete Naming Certificate for $\AbelDirichletComparisonUp$}
\label{ch:concrete-instances-abel-dirichlet-comparison-namecert}
\origin{human}

Following Hardy and Bishop--Bridges, the $\AbelDirichletComparisonUp$ packet records the finite comparison surface shared by the Abel and Dirichlet convergence tests over the $\RealSeriesUp$ corridor. It sits after the real-series source of \autoref{ch:concrete-instances-realseries-namecert}, the Abel-test face of \autoref{ch:concrete-instances-abel-test-namecert}, the Dirichlet-test face of \autoref{ch:concrete-instances-dirichlet-test-namecert}, the uniform Cauchy handoff of \autoref{ch:concrete-instances-uniform-cauchy-series-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names a single shared-tail route for downstream Tauberian, summability, and real-series consumers; it is not a selected series sum, a quotient equality of partial-sum streams, a countable-choice selector, host completeness, or a replacement for either test.

\begin{definition}[Abel--Dirichlet comparison carrier]
\label{def:abel-dirichlet-comparison-carrier}
An $\AbelDirichletComparisonUp$ carrier is a finite $\BHist$ packet
$$
K=(S,A,D,U,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\RealSeriesUp$ source row, exposing the real-valued term stream and the finite partial-sum windows read by the comparison.
\item $A$ is the $\AbelTestUp$ face row, exposing the bounded partial-sum row, monotone null coefficient ledger, and finite Abel summation-by-parts data visible to the packet.
\item $D$ is the $\DirichletTestUp$ face row, exposing the bounded partial-sum row, coefficient stream, null-tail ledger, and finite Dirichlet tail schedule visible to the packet.
\item $U$ is the $\UniformCauchySeriesUp$ shared-tail row, displaying the common tail request and the finite threshold through which both test faces hand off to later Cauchy-style consumers.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the displayed source windows, test-face windows, and shared-tail comparison.
\item $E$ is the $\RealUp$ endpoint seal reached only after $S,A,D,U,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, Abel face, Dirichlet face, shared-tail row, regular readback, endpoint seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a consumer request through $S$ to the finite source windows, through $A$ and $D$ to the two test faces, through $U$ to the shared tail, through $R$ to regular rational readback, and then through $E$ to the endpoint seal.
\item $P$ is the $\Pkg$ provenance over $\AbelDirichletComparisonUp$, $\RealSeriesUp$, $\AbelTestUp$, $\DirichletTestUp$, $\UniformCauchySeriesUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AbelDirichletComparisonUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these ten displayed rows. It has no coordinate for a chosen infinite sum, an equality quotient on partial-sum streams, a choice-selected convergence witness, an ambient completeness theorem, or an independent test result outside the named faces.
\end{definition}

\begin{theorem}[Abel--Dirichlet comparison NameCert obligations]
\label{thm:abel-dirichlet-comparison-namecert-obligations}
For every accepted $\AbelDirichletComparisonUp$ carrier $K=(S,A,D,U,R,E,H,C,P,N)$, the local $\NameCert_{\AbelDirichletComparisonUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed ten-row packet;
\item $\RealSeriesUp$ source exposure through $S$, preserving the finite term and partial-sum windows consumed by the comparison;
\item Abel-face exposure through $A$, preserving the bounded partial-sum, monotone null coefficient, and summation-by-parts rows already named by the Abel-test packet;
\item Dirichlet-face exposure through $D$, preserving the bounded partial-sum, coefficient stream, null-tail, and tail-schedule rows already named by the Dirichlet-test packet;
\item shared-tail exactness through $U$, requiring both faces to hand off to the same $\UniformCauchySeriesUp$ tail request before a later consumer may read a Cauchy-style conclusion;
\item $\RegSeqRatUp$ readback and $\RealUp$ endpoint exposure through $R$ and $E$;
\item componentwise transport, displayed replay, provenance, and local naming through exactly $H,C,P,N$.
\end{enumerate}
These are finite-row obligations over the sibling surfaces of \autoref{ch:concrete-instances-realseries-namecert}, \autoref{ch:concrete-instances-abel-test-namecert}, \autoref{ch:concrete-instances-dirichlet-test-namecert}, \autoref{ch:concrete-instances-uniform-cauchy-series-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\begin{proof}
Project the accepted packet. The carrier exposes exactly the real-series source row, Abel-test face, Dirichlet-test face, shared-tail row, regular readback, endpoint seal, componentwise transports, continuation replay, provenance, and local naming row.

Read the analytic faces. The row $A$ can contribute only the Abel-test finite summation-by-parts route already visible through its carrier, while $D$ can contribute only the Dirichlet-test finite tail route already visible through its carrier. The comparison packet does not add a third convergence argument.

The common obligation is the row $U$. It forces both faces to meet at one $\UniformCauchySeriesUp$ shared-tail request before $R$ and $E$ can be read by downstream consumers.

Finally read $H,C,P,N$. These structural rows transport, replay, source, and name the same route, so the seven listed obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Abel--Dirichlet shared-tail route]
\label{thm:abel-dirichlet-comparison-shared-tail-route}
Every downstream consumer that compares Abel and Dirichlet evidence through an accepted $\AbelDirichletComparisonUp$ carrier must factor through
$$
S\longmapsto A,D\longmapsto U\longmapsto R\longmapsto E
$$
together with $H,C,P,N$. Thus Tauberian, Euler-transform, and summability-style consumers receive a finite shared-tail handoff from the $\RealSeriesUp$ corridor rather than two unrelated informal references to the Abel and Dirichlet rows.
\end{theorem}
\begin{proof}
Start with a downstream comparison read. The source row $S$ is the only $\RealSeriesUp$ entry point, so the requested term and partial-sum data are first confined to the displayed real-series windows.

The two test faces are then read in parallel. The Abel face $A$ and Dirichlet face $D$ retain their own finite coefficient and bounded-partial-sum data, but neither face may export an endpoint seal directly from the comparison packet.

The row $U$ is the unique tail-facing bridge between those faces and later Cauchy-style consumers. A consumer therefore reaches regular rational readback $R$ and the endpoint seal $E$ only after the shared $\UniformCauchySeriesUp$ row has been displayed.

Transport, replay, provenance, and local naming through $H,C,P,N$ preserve that same finite route. Since the carrier has no coordinate for selected sums, quotient stream equality, countable choice, host completeness, or a separate convergence theorem, no downstream consumer can bypass the shared-tail handoff.
\end{proof}

\falsifiablePrediction{An accepted $\AbelDirichletComparisonUp$ consumer that reaches a $\RegSeqRatUp$ readback, $\RealUp$ endpoint seal, or downstream summability handoff without first reading the $\RealSeriesUp$ source row, both test faces, and the $\UniformCauchySeriesUp$ shared-tail row refutes the carrier surface.}

\independenceWitness{realseries, abel-test, dirichlet-test, uniform-cauchy-series, regseqrat, real: no listed sibling supplies the whole ten-row packet $K=(S,A,D,U,R,E,H,C,P,N)$, because each sibling contributes only a source, one test face, a shared-tail handoff, a readback, or a seal while this chapter binds the comparison with transport, replay, provenance, and local naming.}

\closureat{AbelDirichletComparisonUp}{seedStr}

\begin{closurestatus}{\AbelDirichletComparisonUp}
  \constructivestory{An $\AbelDirichletComparisonUp$ packet is generated from a $\RealSeriesUp$ source row, $\AbelTestUp$ and $\DirichletTestUp$ face rows, one $\UniformCauchySeriesUp$ shared-tail row, a $\RegSeqRatUp$ readback, a $\RealUp$ endpoint seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:abel-dirichlet-comparison-carrier}, \autoref{thm:abel-dirichlet-comparison-namecert-obligations}, and \autoref{thm:abel-dirichlet-comparison-shared-tail-route} seed the finite comparison surface over $\RealSeriesUp$, $\AbelTestUp$, $\DirichletTestUp$, $\UniformCauchySeriesUp$, $\RegSeqRatUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected series sums, quotient equality of partial-sum streams, countable choice, ambient real completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the ten-row carrier and prove the finite NameCert obligation surface and shared-tail route.}
\end{closurestatus}
