\chapter{A Concrete Naming Certificate for $\CompactOpenFunctionSpaceUp$}
\label{ch:concrete-instances-compact-open-function-space-namecert}
\origin{human}

Following Kelley and Bourbaki on the compact-open topology, the $\CompactOpenFunctionSpaceUp$ packet records the finite BEDC surface by which a compact source and a target real seal expose a reusable function-space carrier. It reads the compact-open sup-metric boundary of \autoref{ch:concrete-instances-compact-open-metric-namecert}, the continuous-map graph rows of \autoref{ch:concrete-instances-continuousmap-namecert}, and the uniform-tail endpoint route of \autoref{ch:concrete-instances-uniformlimit-namecert}. The packet names the carried compact-open function-space data; it does not install an ambient topology on all host functions, quotient function equality, open-cover compactness, selected limits, or pointwise-only convergence.

\begin{definition}[Compact-open function-space carrier]
\label{def:compact-open-function-space-carrier}
A $\CompactOpenFunctionSpaceUp$ carrier is a finite $\BHist$ packet
$$
K=(X,F,S,U,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\CompactMetricUp$ source row, including the finite source-window and compact-net inspection rows consumed by compact-open requests.
\item $F$ is the finite $\ContinuousMapUp$ graph ledger whose graph rows expose the admissible maps out of $X$.
\item $S$ is the $\CompactOpenMetricUp$ subbasic-radius row, including the finite source-window, target-distance, and radius-budget coordinates used to compare graph rows.
\item $U$ is the $\UniformLimitUp$ tail ledger recording the displayed uniform-tail route by which a function-space endpoint may be read.
\item $W$ is the $\StreamNameUp$ window row through which the sampled graph values and tail comparisons are observed.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the stream windows and tail ledger.
\item $E$ is the $\RealUp$ seal row reached after the regular readback has been displayed.
\item $H$ records componentwise $\hsame$ transport for the compact source row, continuous-map graph rows, compact-open radius rows, uniform-tail ledgers, stream windows, regular readbacks, real seals, replay rows, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay from a compact-open function-space request through graph inspection, subbasic-radius comparison, uniform-tail readback, stream windows, regular rational readback, and the real seal.
\item $P$ is the $\Pkg$ provenance over $\CompactOpenFunctionSpaceUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\CompactOpenMetricUp$, $\UniformLimitUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactOpenFunctionSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,F,S,U,W,R,E,H,C,P,N$. No carrier coordinate names quotient function equality, an unrestricted function-space topology, open-cover compactness, selected limits, pointwise-only convergence, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Compact-open function-space NameCert obligations]
\label{thm:compact-open-function-space-namecert-obligations}
For every accepted $\CompactOpenFunctionSpaceUp$ carrier $K=(X,F,S,U,W,R,E,H,C,P,N)$, the local $\NameCert_{\CompactOpenFunctionSpaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the compact source row, continuous-map graph ledger, compact-open subbasic-radius row, uniform-tail ledger, stream-window row, regular readback, real seal, transport, replay, provenance, and local naming row;
\item graph visibility, requiring every function-space read to enter through the displayed $\ContinuousMapUp$ graph ledger $F$ before it can inspect values;
\item subbasic-radius stability, requiring every compact-open comparison to use the same $\CompactOpenMetricUp$ row $S$ and the finite source-window and radius-budget coordinates stored there;
\item uniform-limit handoff, requiring the endpoint read to pass through the $\UniformLimitUp$ tail ledger $U$, the $\StreamNameUp$ windows $W$, and the $\RegSeqRatUp$ readback $R$ before reaching the $\RealUp$ seal $E$;
\item non-escape, requiring $H,C,P,N$ to preserve the same displayed rows and to export no quotient function equality, unrestricted function-space topology, open-cover compactness, selected limit, pointwise-only convergence, or ambient $\RealUp$ completeness.
\end{enumerate}
No function-space NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:compact-open-function-space-carrier}. The visible analytic coordinates are exactly the compact source row, continuous-map graph ledger, compact-open subbasic-radius row, uniform-tail ledger, stream windows, regular readback, real seal, and structural rows.

Graph visibility is forced by the coordinate $F$. A function-space read has no independent map coordinate, so every value inspection first passes through the displayed $\ContinuousMapUp$ graph rows.

The compact-open comparison is forced by $S$. Its finite source windows and radius budgets are the only subbasic-radius data in the packet, hence classifier transport can preserve compact-open comparisons only by transporting the same row through $H$ and replaying it through $C$.

The endpoint handoff is the displayed route $U,W,R,E$. The uniform-tail ledger supplies the comparison schedule, the stream-window row exposes the finite observations, the regular readback records the rational name, and the real seal is reached only after those rows are visible.

Finally inspect $P$ and $N$. Their source list contains no quotient-function, ambient-topology, open-cover, selected-limit, pointwise-only, or ambient-completeness coordinate, so the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Compact-open function-space uniform-convergence handoff]
\label{thm:compact-open-function-space-uniform-convergence-handoff}
Every uniform-convergence consumer of an accepted $\CompactOpenFunctionSpaceUp$ carrier factors through the displayed route
$$
\ContinuousMapUp,\CompactOpenMetricUp,\UniformLimitUp,\StreamNameUp,\RegSeqRatUp,\RealUp .
$$
Thus the consumer receives continuous-map graph data, compact-open subbasic-radius comparisons, a uniform-tail ledger, finite stream windows, regular rational readback, and a real seal before it treats the endpoint as function-space data. The route exports no quotient function equality, selected host limit, pointwise-only convergence, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(X,F,S,U,W,R,E,H,C,P,N)$. A consumer asking for uniform convergence cannot reach $E$ directly, because the real seal row is downstream of the uniform-tail and readback coordinates.

The graph part of the request first reads $F$, and compact-open comparison then reads $S$. This supplies the finite source-window and radius-budget data needed to interpret the request as a compact-open comparison rather than a pointwise-only observation.

The limiting endpoint is then routed through $U,W,R,E$. The uniform-tail ledger gives the shared tail schedule, the stream windows expose finite observations, the regular readback records the rational name, and the real seal provides the endpoint boundary.

The structural rows $H,C,P,N$ preserve exactly this route. Since the packet contains no quotient equality, selected limit, pointwise-only convergence, or ambient completeness row, none can be exported by the handoff.
\end{proof}

\begin{theorem}[Compact-open function-space nonescape]
\label{thm:compact-open-function-space-nonescape}
An accepted $\CompactOpenFunctionSpaceUp$ carrier exposes only the rows of \autoref{def:compact-open-function-space-carrier}. In particular, any certified read of its function-space endpoint must factor through the compact source row, the $\ContinuousMapUp$ graph ledger, the $\CompactOpenMetricUp$ subbasic-radius row, the $\UniformLimitUp$ tail ledger, the $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback, and the $\RealUp$ seal. It cannot replace that route by open-cover compactness, an unrestricted function-space topology, quotient equality of maps, a selected host limit, pointwise-only convergence, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
The carrier has exactly the rows $X,F,S,U,W,R,E,H,C,P,N$. A certified endpoint read must therefore enter through one of these rows and replay through $C$ while preserving the same components by $H$.

The only graph coordinate is $F$, the only compact-open comparison coordinate is $S$, and the only endpoint route is $U,W,R,E$. Hence every endpoint read factors through the stated finite route.

The excluded principles are absent from the carrier and from the provenance row $P$. The local naming row $N$ therefore has no source from which to certify any of them.
\end{proof}

\closureat{CompactOpenFunctionSpaceUp}{seedStr}

\begin{closurestatus}{\CompactOpenFunctionSpaceUp}
  \constructivestory{A $\CompactOpenFunctionSpaceUp$ packet is generated from a CompactMetricUp source row, ContinuousMapUp graph rows, a CompactOpenMetricUp subbasic-radius row, a UniformLimitUp tail ledger, StreamNameUp windows, RegSeqRatUp readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-open-function-space-carrier}, \autoref{thm:compact-open-function-space-namecert-obligations}, \autoref{thm:compact-open-function-space-uniform-convergence-handoff}, and \autoref{thm:compact-open-function-space-nonescape} seed the compact-open function-space carrier and its finite uniform-convergence handoff.}
  \formalstatus{\encodedDefV}
  \leantarget{BEDC.Derived.CompactOpenFunctionSpaceUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient equality of maps, unrestricted function-space topology, open-cover compactness, selected host limits, pointwise-only convergence, ambient $\RealUp$ completeness, Lean-checked obligations, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, graph visibility, subbasic-radius stability, uniform-limit handoff, and non-escape proofs for the same finite packet.}
\end{closurestatus}
