\chapter{A Concrete Naming Certificate for $\CauchyProductCommutativityUp$}
\label{ch:concrete-instances-cauchy-product-commutativity-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CauchyProductCommutativityUp$ packet names the finite source-window symmetry behind Cauchy-product commutativity before any completed-real multiplication claim is available. It sits over the product packet of \autoref{ch:concrete-instances-cauchyproduct-namecert}, the regular product route of \autoref{ch:concrete-instances-regularcauchyproduct-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic product ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet records commutativity as a finite displayed swap of product-source rows; it does not import host multiplication, quotient streams, selected limits, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[CauchyProductCommutativity carrier]
\label{def:cauchy-product-commutativity-carrier}
A $\CauchyProductCommutativityUp$ carrier is a finite $\BHist$ packet
$$
K=(P_{xy},P_{yx},W_x,W_y,D_{xy},D_{yx},R_{xy},R_{yx},E_{xy},E_{yx},H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P_{xy}$ and $P_{yx}$ are the original and swapped $\CauchyProductUp$ source rows.
\item $W_x$ and $W_y$ are the paired $\StreamNameUp$ finite windows used by both source orders.
\item $D_{xy}$ and $D_{yx}$ are the $\DyadicRatCoreUp$ product-observation rows, one for each order of the displayed dyadic inputs.
\item $R_{xy}$ and $R_{yx}$ are the $\RegSeqRatUp$ classifier rows reached from the two dyadic product observations.
\item $E_{xy}$ and $E_{yx}$ are the $\RealUp$ seal rows exposed only after the paired windows, dyadic product rows, and regular handoffs have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two source rows, paired windows, dyadic product rows, regular handoffs, Real seals, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from every product-commutativity request through $P_{xy},P_{yx},W_x,W_y,D_{xy},D_{yx},R_{xy},R_{yx},E_{xy},E_{yx},H,Q,N$.
\item $Q$ is the $\Pkg$ provenance over $\CauchyProductCommutativityUp$, $\CauchyProductUp$, $\RegularCauchyProductUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyProductCommutativityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. The carrier has no coordinate for host multiplication, quotient stream equality, selected limits, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[CauchyProductCommutativity NameCert obligations]
\label{thm:cauchy-product-commutativity-namecert-obligations}
For every accepted $\CauchyProductCommutativityUp$ carrier
$$
K=(P_{xy},P_{yx},W_x,W_y,D_{xy},D_{yx},R_{xy},R_{yx},E_{xy},E_{yx},H,C,Q,N),
$$
the local $\NameCert_{\CauchyProductCommutativityUp}$ surface consists exactly of carrier admission for the original and swapped $\CauchyProductUp$ source rows, paired $\StreamNameUp$ windows, two $\DyadicRatCoreUp$ product observations, two $\RegSeqRatUp$ classifier rows, two $\RealUp$ seal rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every obligation is read through the sibling routes named in \autoref{ch:concrete-instances-cauchyproduct-namecert}, \autoref{ch:concrete-instances-regularcauchyproduct-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}; no obligation is stored in host multiplication or completed-real algebra.
\end{theorem}
\begin{proof}
Project the accepted carrier. The two product-source rows $P_{xy}$ and $P_{yx}$ expose the same two stream windows in opposite order, and the carrier definition leaves no third source row for a product consumer.

Read the dyadic product observations. The rows $D_{xy}$ and $D_{yx}$ are the only points at which the two window observations are multiplied, and their symmetry is the displayed $\DyadicRatCoreUp$ product-row symmetry rather than a host multiplication law.

Pass to the regular and real-facing rows. The handoffs $R_{xy},R_{yx}$ and seals $E_{xy},E_{yx}$ are downstream of the same windows and dyadic observations. The structural rows $H,C,Q,N$ transport, replay, source, and name this finite packet, so the listed obligations exhaust the local certificate.
\end{proof}

\begin{theorem}[CauchyProductCommutativity window swap]
\label{thm:cauchy-product-commutativity-window-swap}
Swapping the paired $\StreamNameUp$ windows of an accepted $\CauchyProductCommutativityUp$ carrier swaps the two $\CauchyProductUp$ source rows and the two $\DyadicRatCoreUp$ product observations while preserving the same finite route to the $\RegSeqRatUp$ classifier rows, the $\RealUp$ seal rows, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyProductCommutativityUp.CauchyProductCommutativity\_window\_swap}
\begin{proof}
The carrier stores the two windows as the shared source of both product orders. Exchanging $W_x$ and $W_y$ therefore exchanges $P_{xy}$ with $P_{yx}$ and $D_{xy}$ with $D_{yx}$.

The downstream rows are componentwise over the displayed source order. The regular handoffs and Real seals are read after the dyadic product rows, and $H,C,Q,N$ preserve the same dependency route after the exchange.

No host multiplication or quotient-stream equality is used in the swap. The statement is only the finite window exchange already visible inside the packet.
\end{proof}

\begin{theorem}[CauchyProductCommutativity Real seal boundary]
\label{thm:cauchy-product-commutativity-real-seal-boundary}
Every $\RealUp$ consumer of an accepted $\CauchyProductCommutativityUp$ packet factors through the original and swapped $\CauchyProductUp$ source rows, paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ product-observation rows, and $\RegSeqRatUp$ classifier rows before either seal row $E_{xy}$ or $E_{yx}$ is exposed. Thus the packet gives a non-quotient commutativity certificate for later Real algebra routes while excluding host multiplication, quotient streams, selected limits, trichotomy, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from a seal-facing read. By the carrier definition, the only seal rows are $E_{xy}$ and $E_{yx}$, and both are downstream of the displayed product-source rows, windows, dyadic product observations, and regular handoffs.

Use the window-swap theorem to identify the two routes as opposite readings of the same finite source-window packet. The structural rows then replay and name the same dependency route for any Real-facing consumer.

Because the carrier exposes no host multiplication, quotient-stream product, selected limit, trichotomy row, or ambient completeness coordinate, the Real seal boundary cannot export any of those objects.
\end{proof}

\closureat{CauchyProductCommutativityUp}{seedStr}

\begin{closurestatus}{\CauchyProductCommutativityUp}
  \constructivestory{A $\CauchyProductCommutativityUp$ packet is generated from original and swapped $\CauchyProductUp$ source rows, paired $\StreamNameUp$ windows, $\DyadicRatCoreUp$ product-observation rows, $\RegSeqRatUp$ classifier rows, $\RealUp$ seal rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-product-commutativity-carrier}, \autoref{thm:cauchy-product-commutativity-namecert-obligations}, \autoref{thm:cauchy-product-commutativity-window-swap}, and \autoref{thm:cauchy-product-commutativity-real-seal-boundary} seed the finite source-window commutativity certificate for the Cauchy product route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host multiplication, quotient streams, selected limits, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-window swapping, dyadic product-row symmetry, regular handoff preservation, Real seal boundary, transport, replay, provenance, and local naming for BEDC.Derived.CauchyProductCommutativityUp.}
\end{closurestatus}
