\chapter{A Concrete Naming Certificate for $\RegularCauchyFilterRefinementUp$}
\label{ch:concrete-instances-regular-cauchy-filter-refinement-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\RegularCauchyFilterRefinementUp$ packet records the finite route by which regular Cauchy filter data are refined through cofinal subsequence windows before a regular rational readback and terminal real seal are consumed. It sits between the filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the cofinal extraction route of \autoref{ch:concrete-instances-cofinalsubsequence-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The refinement is the filter-facing handoff consumed by \autoref{ch:concrete-instances-metriccompletion-namecert} and \autoref{ch:concrete-instances-uniformcompletion-namecert}; it is not a quotient completion principle, selected representative, countable-choice schedule, or ambient real-completeness claim.

\begin{definition}[Regular Cauchy filter refinement carrier]
\label{def:regular-cauchy-filter-refinement-carrier}
A $\RegularCauchyFilterRefinementUp$ carrier is a finite $\BHist$ packet
$$
Q=(F,S,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the source $\CauchyFilterUp$ row, including its finite filterbase requests and Cauchy pressure ledger.
\item $S$ is the $\CofinalSubsequenceUp$ refinement row selecting the cofinal subsequence windows used to read the filter without changing its source surface.
\item $W$ is the $\StreamNameUp$ finite-window row exposed by $S$ and consumed by the dyadic and regular rational readback.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row for the same windows, including the displayed comparison cells used by the regularity check.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the cofinal windows and dyadic tolerance ledger.
\item $E$ is the terminal $\RealUp$ seal row reached only after $F,S,W,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $F,S,W,D,R,E$ and for the structural rows below.
\item $C$ records displayed $\Cont$ replay from filter refinement to stream windows, from windows and dyadic cells to regular rational readback, and from readback to the Real seal.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyFilterRefinementUp$, $\CauchyFilterUp$, $\CofinalSubsequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyFilterRefinementUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows and their displayed transports. It has no coordinate for quotient filters, quotient completions, selected representatives, countable choice, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Regular Cauchy filter refinement obligations]
\label{thm:regular-cauchy-filter-refinement-obligations}
For every accepted $\RegularCauchyFilterRefinementUp$ carrier $Q=(F,S,W,D,R,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyFilterRefinementUp}$ surface consists exactly of carrier admission for the displayed rows, classifier transport through $H,C,P,N$, cofinal filter refinement through $F$ and $S$, dyadic-window readback through $W,D,R$, and $\RealUp$ non-escape through the seal row $E$. No obligation is discharged by quotient completion, selected representatives, countable choice, host real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:regular-cauchy-filter-refinement-carrier}. The accepted packet lists exactly the filter source, cofinal refinement, stream windows, dyadic tolerance ledger, regular readback, Real seal, and structural rows.

Classifier transport is componentwise. The row $H$ transports the displayed data, $C$ replays the same refinement route, and $P,N$ source and name that route without adding a second classifier surface.

Cofinal filter refinement is read through $F$ and $S$. The source filter stays visible at $F$, while the cofinal subsequence row $S$ selects the windows used by the refinement before any regular rational or Real-facing consumer is reached.

Dyadic-window readback is then forced through $W,D,R$. The stream row exposes finite windows, the dyadic row records their tolerance cells, and the regular rational row is the only readback coordinate downstream of them.

Finally $E$ is the only Real-facing seal. Since the excluded quotient, representative, choice, host-equality, and ambient-completeness principles have no coordinate in the carrier, they cannot be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[Regular Cauchy filter refinement handoff]
\label{thm:regular-cauchy-filter-refinement-handoff}
Every $\MetricCompletionUp$ or $\UniformCompletionUp$ consumer of an accepted $\RegularCauchyFilterRefinementUp$ packet reads the filter refinement only through
$$
F,S,W,D,R,E,H,C,P,N .
$$
The consumer may inspect the source $\CauchyFilterUp$ row, the $\CofinalSubsequenceUp$ refinement row, the finite $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ tolerance ledger, the $\RegSeqRatUp$ readback, the terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row. It receives no quotient completion, selected representative, countable-choice schedule, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Start with the displayed carrier. The refinement route exposes $F$ before any cofinal window is read, so completion-facing consumers do not begin from a quotient filter or selected representative.

Apply the cofinal row $S$ and then the finite window row $W$. These rows align the filter request surface with the cofinal subsequence interface of \autoref{ch:concrete-instances-cofinalsubsequence-namecert} before the readback reaches dyadic tolerance data.

The readback step uses $D$ and $R$. The dyadic ledger supplies finite comparison cells, and the regular rational readback is the only numerical row exported before the seal $E$.

The completion consumers of \autoref{ch:concrete-instances-metriccompletion-namecert} and \autoref{ch:concrete-instances-uniformcompletion-namecert} can therefore read only the displayed route and its structural rows $H,C,P,N$. No absent quotient, representative, choice, or ambient completeness coordinate can be recovered downstream.
\end{proof}

\closureat{RegularCauchyFilterRefinementUp}{seedStr}

\begin{closurestatus}{\RegularCauchyFilterRefinementUp}
  \constructivestory{A $\RegularCauchyFilterRefinementUp$ packet is generated from a CauchyFilter source row, CofinalSubsequence refinement row, StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-filter-refinement-carrier}, \autoref{thm:regular-cauchy-filter-refinement-obligations}, and \autoref{thm:regular-cauchy-filter-refinement-handoff} seed the finite filter-refinement route from CauchyFilter data through cofinal windows and dyadic readback to completion-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, countable choice, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, cofinal filter refinement, dyadic-window readback, RealUp non-escape, and TasteGate field faithfulness for BEDC.Derived.RegularCauchyFilterRefinementUp.}
\end{closurestatus}
