\chapter{A Concrete Naming Certificate for $\SpectralStabilizationUp$}
\label{ch:concrete-instances-spectral-stabilization-namecert}
\origin{ai}

The $\SpectralStabilizationUp$ packet realizes the killed bit-flip closure-chain spectral-radius and survival-potential ledger of \autoref{subsec:philosophy-dna-window-six-boundary-tiles} as finite BEDC NameCert data. It consumes the six-coordinate codon source window of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the stop-boundary transition surface of \autoref{ch:concrete-instances-codon-transition-matrix-namecert}, the local inverse spectrum of \autoref{ch:concrete-instances-codon-window-spectral-inverse-namecert}, and the stop-suffix carrier of \autoref{ch:concrete-instances-stopcodonzeckendorfsuffix-namecert}. The packet records a finite spectral stabilization surface for displayed killed one-bit dynamics; it does not identify the biological code table with a kernel primitive, choose a global stochastic model, or import an analytic Perron theorem outside the displayed finite ledger.

\begin{definition}[Spectral stabilization carrier]
\label{def:spectral-stabilization-carrier}
A $\SpectralStabilizationUp$ carrier is a finite $\BHist$ packet
$$
Z=(W,M,I,K,R,L,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ source-window row exposing the finite $Q_{6}$ codon-window carrier and the six bit coordinates used by the killed bit-flip walk.
\item $M$ is the $\CodonTransitionMatrixUp$ row exposing the local transition vocabulary for scan, elongate, terminate, readthrough, repair, and mutate states.
\item $I$ is the $\CodonWindowSpectralInverseUp$ row exposing local face spectra, Hamming adjacency spectra, reassignment spectra, and stop-face reconstruction data.
\item $K$ is the killed bit-flip matrix ledger. It records, for each displayed support in the closure chain, the finite transient matrix entries whose off-support moves are absorbed.
\item $R$ is the spectral-radius row. It records the displayed one-step retention, Perron-root approximation row, and survival-potential ledger used by \autoref{thm:philosophy-spectral-stabilization-closure-chain}.
\item $L$ is the closure-chain ledger for $\mathcal{R}$, $\overline{\mathcal{R}}$, $\operatorname{Med}_{1}(\mathcal{R})$, and $M$, including the displayed vertex and internal-edge counts.
\item $U$ is the stop-suffix and anchor handoff row, read through $\StopCodonZeckendorfSuffixUp$ and the finite stop-start core named by the source vision.
\item $H$ records componentwise $\hsame$ transport for source windows, transition rows, inverse spectra, killed matrices, spectral-radius ledgers, closure-chain rows, stop-suffix handoffs, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a spectral-stabilization request through $W,M,I,K,R,L,U,H$.
\item $P$ is the $\Pkg$ provenance over $\SpectralStabilizationUp$, $\CodonSixBitWindowUp$, $\CodonTransitionMatrixUp$, $\CodonWindowSpectralInverseUp$, $\StopCodonZeckendorfSuffixUp$, the source vision of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SpectralStabilizationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,M,I,K,R,L,U,H,C,P,N$. It has no coordinate for a hidden biological table, a selected global stochastic process, analytic spectral theory outside the finite matrix ledger, quotient codon equality, probabilistic inference, or a choice principle.
\end{definition}

\begin{theorem}[Spectral stabilization NameCert obligations]
\label{thm:spectral-stabilization-namecert-obligations}
For every accepted $\SpectralStabilizationUp$ carrier $Z=(W,M,I,K,R,L,U,H,C,P,N)$, the local $\NameCert_{\SpectralStabilizationUp}$ surface consists exactly of source-window admission through $W$, transition admission through $M$, inverse-spectrum admission through $I$, killed-matrix entry exactness through $K$, spectral-radius and survival-potential ledger display through $R$, closure-chain support display through $L$, stop-suffix handoff through $U$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:spectral-stabilization-carrier}. The source-window, transition, inverse-spectrum, killed-matrix, spectral-radius, closure-chain, stop-suffix, transport, replay, provenance, and local naming rows are exactly the displayed coordinates.

The killed matrix ledger $K$ can be read only after the codon-window row $W$ supplies the six bit coordinates and the transition row $M$ supplies the local state vocabulary. The inverse-spectrum row $I$ supplies the finite face and adjacency spectra used by the same matrix rows.

The spectral-radius row $R$ is not an external analytic theorem. It is a displayed finite ledger containing the one-step retention, Perron-root approximation, and survival-potential data for the supports named by $L$.

The stop-suffix row $U$ routes the anchor and stop-start core through the existing suffix packet. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite inventory, so no hidden biological table, global stochastic process, quotient codon equality, probabilistic inference row, or choice principle is exported.
\end{proof}

\begin{theorem}[Spectral stabilization window handoff]
\label{thm:spectral-stabilization-window-handoff}
Every accepted $\SpectralStabilizationUp$ spectral-radius or survival-potential read factors through
$$
W,M,I \longmapsto K,L,R,U \longmapsto H,C,P,N .
$$
Thus a consumer receives the codon source window, transition vocabulary, inverse-spectrum row, killed bit-flip matrix entries, closure-chain support ledger, spectral-radius and survival-potential rows, stop-suffix handoff, transport, replay, provenance, and local naming. It receives no hidden biological table, selected global stochastic model, analytic spectral theorem outside the displayed matrix ledger, quotient codon equality, probabilistic inference row, or choice principle.
\end{theorem}
\begin{proof}
Start with a spectral-radius or survival-potential read. The codon-window row $W$ fixes the finite six-coordinate source, while $M$ fixes the transition vocabulary and $I$ fixes the local spectrum rows.

The killed bit-flip matrix ledger $K$ is then computed over the displayed supports in $L$. Its entries are finite rows: moves inside a support remain transient, and moves outside that support are absorbed.

The row $R$ stores the one-step retention, spectral-radius approximation, and survival-potential data for the same support chain. The row $U$ attaches the stop-suffix and anchor handoff without adding a global code table.

Finally $H,C,P,N$ preserve and name the same packet. Since no additional coordinate exists, the handoff remains finite and cannot export the refused principles.
\end{proof}

\falsifiablePrediction{Every accepted $\SpectralStabilizationUp$ read of a spectral radius, one-step retention, or survival-potential row factors through one $\CodonSixBitWindowUp$ source window, one $\CodonTransitionMatrixUp$ transition vocabulary, one $\CodonWindowSpectralInverseUp$ inverse-spectrum row, one killed bit-flip matrix ledger, one closure-chain support ledger, one $\StopCodonZeckendorfSuffixUp$ handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{codon-six-bit-window, codon-transition-matrix, codon-window-spectral-inverse, stopcodonzeckendorfsuffix: $\SpectralStabilizationUp$ is not bijective to any listed sibling because it jointly carries killed matrix entries, closure-chain supports, spectral-radius rows, survival-potential rows, stop-suffix handoff, transport, replay, provenance, and local naming.}

The Lean TasteGate route for \texttt{BEDC.Derived.SpectralStabilizationUp} must provide explicit $\Nontrivial\ \SpectralStabilizationUp$ and $\FieldFaithful\ \SpectralStabilizationUp$ instances preserving $W,M,I,K,R,L,U,H,C,P,N$ as separate displayed fields.

\closureat{SpectralStabilizationUp}{seedStr}

\begin{closurestatus}{\SpectralStabilizationUp}
  \constructivestory{A $\SpectralStabilizationUp$ packet is generated from a codon source-window row, transition vocabulary row, inverse-spectrum row, killed bit-flip matrix ledger, closure-chain support ledger, spectral-radius and survival-potential rows, stop-suffix handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:spectral-stabilization-carrier}, \autoref{thm:spectral-stabilization-namecert-obligations}, and \autoref{thm:spectral-stabilization-window-handoff} seed the finite spectral-stabilization packet over codon windows, transition matrices, inverse spectra, killed bit-flip matrices, closure-chain support rows, and stop-suffix handoffs.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological table identity, selected global stochastic modeling, analytic spectral theory outside finite matrix ledgers, quotient codon equality, probabilistic inference, choice, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the eleven-row carrier and prove source-window admission, transition admission, inverse-spectrum admission, killed-matrix exactness, spectral-ledger display, closure-chain support display, stop-suffix handoff, Nontrivial SpectralStabilizationUp, and FieldFaithful SpectralStabilizationUp for BEDC.Derived.SpectralStabilizationUp.}
\end{closurestatus}
