\chapter{A Concrete Naming Certificate for $\TotallyDisconnectedSpaceUp$}
\label{ch:concrete-instances-totally-disconnected-space-namecert}
\origin{human}

Following Stone, Engelking, and Willard on zero-dimensional and totally disconnected spaces, the $\TotallyDisconnectedSpaceUp$ packet records the finite BEDC surface by which a displayed topology admits no nontrivial connected component rows. It sits over the generated-open classifier of \autoref{ch:concrete-instances-topology-namecert}, the compact finite-cover boundary of \autoref{ch:concrete-instances-compact-namecert}, the separated-neighborhood surface of \autoref{ch:concrete-instances-hausdorffspace-namecert}, and the clopen-ledger bridge of \autoref{ch:concrete-instances-stoneduality-namecert}. The packet names clopen separation and component-collapse rows without importing ultrafilters, host point equality, quotient spaces, selected components, open-cover compactness beyond the displayed compact row, or excluded middle.

\begin{definition}[TotallyDisconnectedSpace carrier]
\label{def:totally-disconnected-space-carrier}
A $\TotallyDisconnectedSpaceUp$ carrier is a finite $\BHist$ packet
$$
T=(O,K,Hd,x,y,U,V,L,Z,R,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the $\TopologyUp$ source row, including open predicates, finite neighborhood histories, and the generated-open classifier used by topology consumers.
\item $K$ is the optional $\CompactUp$ support row read by compact Stone-style consumers; it is a displayed compactness interface, not an ambient open-cover principle.
\item $Hd$ is the $\HausdorffSpaceUp$ separation row exposing disjoint open-neighborhood data for distinct displayed point names.
\item $x,y$ are point-name rows in the same topology source.
\item $U,V$ are clopen separation rows: $U$ contains $x$, $V$ contains $y$, and each row carries both open and complement-open evidence in $O$.
\item $L$ is the clopen ledger row connecting finite clopen observations with the Stone-duality clopen surface of \autoref{ch:concrete-instances-stoneduality-namecert}.
\item $Z$ is the component-collapse row stating that every displayed connected-subpacket read through $O$ has at most one point-name class under the local classifier.
\item $R$ is the refusal row excluding ultrafilter points, quotient components, host equality, selected component representatives, and excluded-middle separation.
\item $C$ records displayed $\Cont$ replay from a point-pair query through $O,Hd,U,V,L,Z,R$.
\item $P$ is the $\Pkg$ provenance over $\TotallyDisconnectedSpaceUp$, $\TopologyUp$, $\CompactUp$, $\HausdorffSpaceUp$, $\StoneDualityUp$, $\BHist$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\TotallyDisconnectedSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a completed Stone space, ultrafilter selection, quotient-component equality, host subset equality, or a choice-selected clopen basis.
\end{definition}

\begin{theorem}[TotallyDisconnectedSpace NameCert obligations]
\label{thm:totally-disconnected-space-namecert-obligations}
For every accepted $\TotallyDisconnectedSpaceUp$ carrier
$$
T=(O,K,Hd,x,y,U,V,L,Z,R,C,P,N),
$$
the local $\NameCert_{\TotallyDisconnectedSpaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the topology source, optional compact support, Hausdorff separation row, point names, clopen separation rows, clopen ledger, component-collapse row, refusal row, replay, provenance, and local naming row;
\item clopen separation, requiring every separated pair of displayed point names to be routed through clopen rows $U,V$ inside $O$;
\item component collapse, requiring every connected-subpacket read through the topology source to factor through the singleton classifier row $Z$;
\item Stone-ledger compatibility, requiring the clopen ledger $L$ to expose only the finite clopen rows consumed by the Stone-duality surface;
\item nonescape, requiring all topology, compact, Hausdorff, and Stone-duality consumers to read only $O,K,Hd,x,y,U,V,L,Z,R,C,P,N$.
\end{enumerate}
No totally disconnected space obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:totally-disconnected-space-carrier}. The accepted tuple displays the topology source, compact support row, Hausdorff separation data, point names, clopen rows, clopen ledger, component-collapse row, refusal row, replay, provenance, and local naming data.

The clopen separation row is local to $O$. A separated pair first reads the $\HausdorffSpaceUp$ row $Hd$ for disjoint neighborhoods and then refines the displayed neighborhoods to the clopen rows $U,V$. The proof uses the rows as carrier fields; it does not select a global clopen basis.

Component collapse is exactly the role of $Z$. Any connected-subpacket consumer must pass through the same topology source and the same clopen ledger before it can compare point names, so the only exported comparison is the singleton classifier row.

The Stone-ledger and nonescape clauses are inventory checks on $L,R,C,P,N$. Since no ultrafilter point, quotient component, host equality row, selected representative, or excluded-middle branch occurs in the carrier, none can be exported by the local certificate.
\end{proof}

\begin{theorem}[TotallyDisconnectedSpace clopen separation route]
\label{thm:totally-disconnected-space-clopen-separation-route}
Let $T=(O,K,Hd,x,y,U,V,L,Z,R,C,P,N)$ be an accepted $\TotallyDisconnectedSpaceUp$ packet. Every Stone-duality or compact-Hausdorff consumer that asks for total disconnectedness factors first through the topology row $O$, then through the Hausdorff separation row $Hd$, then through the displayed clopen separation rows $U,V$, and finally through the clopen ledger $L$ and component-collapse row $Z$. The route exports no ultrafilter point, quotient component, host point equality, selected clopen basis, or nonconstructive separation principle.
\end{theorem}
\begin{proof}
Start from the topology row $O$ and the point names $x,y$. The Hausdorff row $Hd$ supplies only displayed neighborhood separation, so a total-disconnectedness consumer must still use the clopen rows $U,V$ before it can read a separation as a clopen separation.

The clopen ledger $L$ records the finite rows consumed by Stone-duality-style arguments. It keeps the consumer inside the displayed topology classifier and does not build a point space or an ultrafilter representation.

Finally $Z$ supplies the component-collapse comparison. Replay through $C$ and naming through $P,N$ preserve the same route, while the refusal row $R$ excludes quotient components, host equality, selected clopen bases, and nonconstructive separation branches.
\end{proof}

\closureat{TotallyDisconnectedSpaceUp}{seedStr}

\begin{closurestatus}{\TotallyDisconnectedSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:totally-disconnected-space-carrier}, \autoref{thm:totally-disconnected-space-namecert-obligations}, and \autoref{thm:totally-disconnected-space-clopen-separation-route} seed the finite topology, compact, Hausdorff, clopen-ledger, and component-collapse surface for totally disconnected spaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ultrafilter existence, quotient components, host point equality, selected clopen bases, open-cover compactness beyond displayed compact rows, Lean verification, or standard bridge closure.}
  \upgradepath{Obligation closure requires checked carrier admission, clopen separation, component collapse, Stone-ledger compatibility, and nonescape for BEDC.Derived.TotallyDisconnectedSpaceUp.}
  \constructivestory{A $\TotallyDisconnectedSpaceUp$ packet is generated from a topology row, optional compact support, Hausdorff separated-neighborhood data, displayed point names, clopen separation rows, a clopen ledger, component-collapse evidence, replay, provenance, and a local NameCert row.}
\end{closurestatus}
