\chapter{A Concrete Naming Certificate for $\NestedIntervalTheoremUp$}
\label{ch:concrete-instances-nested-interval-theorem-namecert}
\origin{human}

Following Bishop and Bridges, the $\NestedIntervalTheoremUp$ packet records the constructive nested closed interval theorem as finite BEDC route data. It consumes the retained-window surface of \autoref{ch:concrete-instances-nestedinterval-namecert}, the dyadic endpoint and tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the interval-existence handoff without asserting quotient reals, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Nested interval theorem carrier]
\label{def:nested-interval-theorem-carrier}
A $\NestedIntervalTheoremUp$ carrier is a finite $\BHist$ packet
$$
K=(I,D,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the accepted $\NestedIntervalUp$ row, including the inspected closed rational or dyadic interval windows, endpoint-order rows, width rows, and displayed containment witnesses.
\item $D$ is the $\DyadicRatCoreUp$ ledger that records the endpoint comparisons and the diameter-to-tolerance rows used by the retained windows.
\item $S$ is the $\StreamNameUp$ finite-window schedule requested from the lower and upper endpoint rows.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same finite interval windows and dyadic tolerance ledger.
\item $E$ is the $\RealUp$ seal row reached only after $I,D,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval, dyadic, stream, regular readback, Real seal, replay, provenance, and naming rows.
\item $C$ records the displayed $\Cont$ replay from nested interval data through dyadic tolerance control, stream windows, regular readback, and Real seal handoff.
\item $P$ is the $\Pkg$ provenance over $\NestedIntervalTheoremUp$, $\NestedIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedIntervalTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an infinite host intersection object, a selected quotient representative, countable choice, trichotomy, a Cauchy-completion quotient, or ambient $\RealUp$ completeness.
\end{definition}
\leandef{BEDC.Derived.NestedIntervalTheoremUp}

\begin{theorem}[Nested interval theorem NameCert obligations]
\label{thm:nested-interval-theorem-namecert-obligations}
For every accepted $\NestedIntervalTheoremUp$ carrier $K=(I,D,S,R,E,H,C,P,N)$, the local $\NameCert_{\NestedIntervalTheoremUp}$ surface consists exactly of carrier admission for the displayed nine-row packet, $\NestedIntervalUp$ source exposure through $I$, $\DyadicRatCoreUp$ endpoint and tolerance exactness through $D$, $\StreamNameUp$ finite-window exposure through $S$, $\RegSeqRatUp$ readback through $R$, terminal $\RealUp$ seal handoff through $E$, and the structural transport, replay, provenance, and naming rows $H,C,P,N$.

No obligation may be discharged by a host interval intersection, selected point, countable choice, trichotomy, quotient real, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:nested-interval-theorem-carrier}. The rows $I,D,S,R,E,H,C,P,N$ are the only coordinates visible to the local classifier.

The interval source is $I$. It exposes only the finite nested-window surface already available from $\NestedIntervalUp$: endpoint order, width, containment, and retained-window rows.

The completion-facing route is finite. The ledger $D$ reads the dyadic endpoint and tolerance comparisons, $S$ lists the requested stream windows, $R$ repacks those windows as a regular rational readback, and $E$ is downstream of those rows.

The structural rows do not add mathematical principles. The transports $H$, continuations $C$, provenance $P$, and local certificate $N$ preserve and name the same packet, so the excluded host intersection, choice, quotient, trichotomy, and completeness coordinates remain absent.
\end{proof}

\begin{theorem}[Nested interval theorem Real seal handoff]
\label{thm:nested-interval-theorem-real-seal-handoff}
Every $\RealUp$ consumer of an accepted $\NestedIntervalTheoremUp$ packet factors through the finite route
$$
\NestedIntervalUp \longmapsto \DyadicRatCoreUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Concretely, the consumer reads the nested interval row $I$, the dyadic endpoint and tolerance ledger $D$, the stream-window schedule $S$, the regular-rational row $R$, and only then the Real seal row $E$ with its transports, continuations, provenance, and local naming.
\end{theorem}
\begin{proof}
Start with the Real-facing read. Since $E$ is the only Real seal coordinate in the carrier, every such read must pass through the rows that make $E$ visible.

The source row is $I$. It supplies the finite nested closed interval windows and containment witnesses, while $D$ supplies the dyadic endpoint comparisons and diameter-to-tolerance rows read from the same windows.

The name construction then passes through $S$ and $R$. The finite stream schedule selects the requested endpoint windows, and the regular rational row records the corresponding Cauchy readback.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Because the carrier contains no coordinate for a host intersection object, selected point, quotient real, countable choice, trichotomy, or ambient completeness, the displayed handoff is exhaustive.
\end{proof}

\closureat{NestedIntervalTheoremUp}{seedStr}

\begin{closurestatus}{\NestedIntervalTheoremUp}
  \constructivestory{A $\NestedIntervalTheoremUp$ packet is generated from a NestedInterval row, a DyadicRatCore endpoint and tolerance ledger, StreamName finite windows, a RegSeqRat readback row, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-interval-theorem-carrier}, \autoref{thm:nested-interval-theorem-namecert-obligations}, and \autoref{thm:nested-interval-theorem-real-seal-handoff} seed the finite constructive nested closed interval route from displayed nested windows to RegSeqRat readback and Real seal handoff.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.NestedIntervalTheoremUp}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient reals, selected host intersections, countable choice, trichotomy, ambient $\RealUp$ completeness, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nested-window exposure, dyadic endpoint and tolerance exactness, StreamName window exposure, RegSeqRat readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.NestedIntervalTheoremUp.}
\end{closurestatus}
