\chapter{A Concrete Naming Certificate for $\LiouvilleNumberUp$}
\label{ch:concrete-instances-liouville-number-namecert}
\origin{human}

Beginning from Liouville's rational-approximation construction, the $\LiouvilleNumberUp$ packet records a nontrivial $\RealUp$ name by finite approximation rows rather than by an ambient transcendence theorem. It reads rational approximants through the rational-approximation sibling \autoref{ch:concrete-instances-real-rational-approximation-namecert}, stores tolerance budgets in the $\DyadicRatCoreUp$ ledger, consumes finite $\StreamNameUp$ windows and $\RegSeqRatUp$ readback rows, and seals the resulting regular real name through \autoref{ch:concrete-instances-real-namecert}. The packet is a finite NameCert route for Liouville-style approximation data, not a proof of full transcendence theory, decimal expansion uniqueness, countable choice over approximants, or completeness of all $\RealUp$ streams.

\begin{definition}[LiouvilleNumber carrier]
\label{def:liouville-number-carrier}
A $\LiouvilleNumberUp$ carrier is a finite $\BHist$ packet
$$
L=(Q,D,S,R,A,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the rational-approximant row: for each accepted finite precision request it displays the inspected rational approximant and the denominator-growth witness used by the Liouville construction.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic budgets against which the rational errors are compared.
\item $S$ is the $\StreamNameUp$ finite-window schedule that lists exactly which approximant windows and tolerance windows are opened by the certificate.
\item $R$ is the $\RegSeqRatUp$ readback row, turning the scheduled rational approximants into a regular rational sequence before any $\RealUp$ seal is consumed.
\item $A$ is the Liouville approximation classifier, pairing each displayed denominator-growth row with the dyadic comparison that witnesses an error below the recorded budget.
\item $E$ is the $\RealUp$ seal row, admitting the regular rational readback as the named real object after the finite approximation route has been checked.
\item $H$ stores componentwise $\hsame$ transport for $Q,D,S,R,A,E$ and the local naming rows.
\item $C$ stores displayed $\Cont$ replay from a real-name request through the approximant row, tolerance ledger, finite window schedule, regular rational readback, approximation classifier, and real seal.
\item $P$ is the $\Pkg$ provenance over $\LiouvilleNumberUp$, $\RatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LiouvilleNumberUp}$ row.
\end{enumerate}
The carrier asserts only that these displayed rows form one Liouville-style real-name certificate. It has no coordinate for decimal expansion uniqueness, unbounded choice of approximants outside the displayed windows, a blanket irrationality theorem for all reals, a transcendence theorem, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[LiouvilleNumber NameCert obligations]
\label{thm:liouville-number-namecert-obligations}
For every accepted $\LiouvilleNumberUp$ carrier $L=(Q,D,S,R,A,E,H,C,P,N)$, the local $\NameCert_{\LiouvilleNumberUp}$ surface consists exactly of carrier admission, rational-approximant exposure through $Q$, dyadic tolerance comparison through $D$, finite window scheduling through $S$, regular rational readback through $R$, Liouville approximation classification through $A$, $\RealUp$ seal exposure through $E$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, local naming, and ledger refusal for decimal uniqueness, unbounded choice, general irrationality, transcendence, and ambient real completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:liouville-number-carrier}. The accepted packet exposes exactly the rational approximant row, dyadic ledger, finite window schedule, regular rational readback, approximation classifier, real seal, transport, replay, provenance, and local naming rows.

The approximation rows are finite because $Q$ and $S$ list only the inspected windows. Each accepted precision request is matched with the denominator-growth witness and error budget recorded in $D$ and $A$.

The regular rational readback $R$ converts those scheduled approximants into the row consumed by the real-name surface. The handoff to $E$ therefore occurs only after the finite Liouville approximation route has been replayed.

Rows $H,C,P,N$ transport, replay, source, and name the same packet. Since no other coordinate exists, the certificate cannot export decimal expansion uniqueness, an off-window choice function, a general irrationality theorem, a transcendence theorem, or ambient completeness of $\RealUp$.
\end{proof}

\begin{theorem}[LiouvilleNumber finite approximation handoff]
\label{thm:liouville-number-finite-approximation-handoff}
Every real-name consumer of an accepted $\LiouvilleNumberUp$ carrier factors through the finite route
$$
Q \longmapsto D \longmapsto S \longmapsto R \longmapsto A \longmapsto E \longmapsto H,C,P,N .
$$
Thus the packet supplies a Liouville-style $\RealUp$ object from rational approximants, dyadic tolerance budgets, finite stream windows, and regular rational readback, without claiming decimal expansion uniqueness, unbounded choice, transcendence, or ambient real completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $L=(Q,D,S,R,A,E,H,C,P,N)$. A real-name request must read the rational approximant row $Q$ and the dyadic budget row $D$ before it can inspect the window schedule $S$.

The regular rational readback $R$ is then forced by the displayed windows. The classifier $A$ records the Liouville approximation inequality for the same inspected rows, so the real seal $E$ receives only finite approximation evidence.

The transport, replay, provenance, and naming rows preserve that route. They add no coordinate for off-window choice, decimal uniqueness, transcendence, or a general completeness theorem, so every downstream consumer remains inside the finite NameCert packet.
\end{proof}

\closureat{LiouvilleNumberUp}{seedStr}

\begin{closurestatus}{\LiouvilleNumberUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:liouville-number-carrier}, \autoref{thm:liouville-number-namecert-obligations}, and \autoref{thm:liouville-number-finite-approximation-handoff} seed the finite Liouville-style real-name certificate over rational approximants, dyadic tolerance budgets, finite StreamName windows, RegSeqRat readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, decimal expansion uniqueness, countable choice over approximants, a general irrationality theorem, transcendence, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, rational-approximant exposure, dyadic comparison exactness, finite window scheduling, regular rational readback, Real seal handoff, structural transport, replay, provenance, and nonescape for BEDC.Derived.LiouvilleNumberUp.}
  \constructivestory{A $\LiouvilleNumberUp$ packet is generated from rational approximant rows, DyadicRatCore tolerance budgets, finite StreamName windows, RegSeqRat readbacks, a Real seal, componentwise hsame transport, displayed Cont replay, package provenance, and local NameCert evidence.}
\end{closurestatus}
