\chapter{A Concrete Naming Certificate for $\CofinalDyadicMeshUp$}
\label{ch:concrete-instances-cofinal-dyadic-mesh-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\CofinalDyadicMeshUp$ packet names the finite selector that refines an arbitrary Real- or completion-facing observation request to a dyadic mesh window. It sits between the dyadic mesh discipline of \autoref{ch:concrete-instances-dyadicmesh-namecert}, the endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter records the selector as finite NameCert data; it does not assert a quotient real equality, selected limit, or countable-choice subnet.

\begin{definition}[Cofinal dyadic mesh carrier]
\label{def:cofinal-dyadic-mesh-carrier}
A $\CofinalDyadicMeshUp$ carrier is a finite $\BHist$ packet
$$
K=(Q,D,M,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the finite observation request coming from a Real or regular Cauchy consumer.
\item $D$ is the $\DyadicRatCoreUp$ dyadic endpoint and tolerance ledger available to answer $Q$.
\item $M$ is the $\DyadicMeshUp$ mesh row selected from $D$ and refined far enough for the request.
\item $S$ is the $\StreamNameUp$ finite-window row opened at the selected mesh depth.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row attached to the same window.
\item $E$ is the $\RealUp$ seal row read only after $M,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the request, dyadic ledger, mesh, window, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from $Q$ through $D,M,S,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CofinalDyadicMeshUp$, $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CofinalDyadicMeshUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,D,M,S,R,E,H,C,P,N$. It has no coordinate for a hidden subnet, quotient Cauchy class, host real equality, selected limit, countable-choice schedule, or ambient completeness witness.
\end{definition}

\begin{theorem}[Cofinal dyadic mesh NameCert obligations]
\label{thm:cofinal-dyadic-mesh-namecert-obligations}
For every accepted $\CofinalDyadicMeshUp$ carrier $K=(Q,D,M,S,R,E,H,C,P,N)$, the local $\NameCert_{\CofinalDyadicMeshUp}$ surface consists exactly of carrier admission, request exposure through $Q$, dyadic endpoint and tolerance exposure through $D$, selected mesh exposure through $M$, finite-window exposure through $S$, regular readback through $R$, terminal Real-seal exposure through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$. Every Real or regular Cauchy finite observation admitted by the packet must pass through this displayed dyadic mesh selector before reading $S,R,E$.
\end{theorem}
\begin{proof}
Project the carrier. The request row $Q$ is the only incoming observation demand, while $D$ and $M$ display the dyadic endpoint ledger and the selected mesh depth used to answer it.

The finite observation then proceeds through $S,R,E$. The stream window $S$ is opened at the selected mesh depth, the regular readback $R$ consumes that window, and the terminal Real seal $E$ is read only after those rows are visible.

The structural rows $H,C,P,N$ transport, replay, package, and name exactly the displayed route. Since no hidden subnet, quotient class, host equality, selected limit, choice schedule, or ambient completeness row appears in the carrier, every admitted observation factors through the finite dyadic selector.
\end{proof}

\falsifiablePrediction{If the selected mesh row $M$ is removed, a Real or regular Cauchy finite observation can no longer be forced to pass through a displayed dyadic refinement before the StreamName, RegSeqRat, and Real seal rows are read.}

\independenceWitness{dyadicmesh, dyadicratcore, streamname, regseqrat, real: none is bijective to $\CofinalDyadicMeshUp$ because this packet stores the observation request, dyadic endpoint ledger, selected mesh depth, finite stream window, regular readback, terminal Real seal, transport, replay, provenance, and local NameCert row as one selector route.}

\closureat{CofinalDyadicMeshUp}{seedStr}

\begin{closurestatus}{\CofinalDyadicMeshUp}
  \constructivestory{A $\CofinalDyadicMeshUp$ packet is generated from a finite observation request, a $\DyadicRatCoreUp$ endpoint and tolerance ledger, a selected $\DyadicMeshUp$ row, $\StreamNameUp$ finite-window data, $\RegSeqRatUp$ readback, a terminal $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cofinal-dyadic-mesh-carrier} and \autoref{thm:cofinal-dyadic-mesh-namecert-obligations} seed the finite dyadic-mesh selector feeding Real and RegSeqRat finite observations.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient real equality, selected limits, hidden subnets, countable-choice schedules, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, selector cofinality, finite-window routing, regular readback, Real-seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.CofinalDyadicMeshUp.}
\end{closurestatus}
