\chapter{A Concrete Naming Certificate for $\CandidateSNConfluenceBoundaryUp$}
\label{ch:concrete-instances-candidate-sn-confluence-boundary-namecert}
\origin{ai}

The $\CandidateSNConfluenceBoundaryUp$ packet realizes the normalization and confluence frontier of \autoref{ch:metacic-open-problems} as one finite MetaCIC NameCert row. It sits beside the critical-path carrier of \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, the normalisation frontier, the redex frontier, and the bounded normal-equality checker, and records exactly where candidate-mediated strong-normalization evidence can be consumed before confluence claims must stop. The packet names candidate evidence, bounded normal checks, critical-pair or redex-frontier handoff rows, and nonescape rows; it is not a closed subject-reduction theorem, arbitrary Church--Rosser theorem, or closed consistency theorem.

\falsifiablePrediction{Any consumer of an accepted $\CandidateSNConfluenceBoundaryUp$ packet still cannot export closed subject reduction or arbitrary Church--Rosser unless it also supplies the displayed subject-reduction discharge rows, confluence-boundary rows, and candidate-interface admission rows of the carrier.}

\independenceWitness{metaciccriticalpath, metacicnormalizationfrontier, metacicredexfrontier, boundednormalequalitychecker: the critical path records the global frontier, the normalization frontier records candidate-mediated strong-normalization boundaries, the redex frontier records local reduction cases, and the bounded checker records finite normal-equality comparison; none is bijective to the packet that stores all four rows with one confluence nonescape boundary.}

\begin{definition}[CandidateSNConfluenceBoundary carrier]
\label{def:candidate-sn-confluence-boundary-carrier}
A $\CandidateSNConfluenceBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(K,N,R,E,S,J,U,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the MetaCIC critical-path row naming the subject-reduction, normalization, confluence, decidability, and consistency frontier being read.
\item $N$ is the candidate strong-normalization row, admitting only terms already inside the candidate interface.
\item $R$ is the redex-frontier row through which local reduction and critical-pair cases are inspected.
\item $E$ is the bounded normal-equality checker row used when a finite normal comparison is requested.
\item $S$ is the subject-reduction discharge row, recording which subject-reduction inputs are present and which remain outside the packet.
\item $J$ is the confluence-boundary row, recording displayed join, common-reduct, or normal-fragment handoffs without promoting them to arbitrary Church--Rosser.
\item $U$ is the nonescape row excluding closed subject reduction, arbitrary closed confluence, full closed consistency, and candidate-free strong normalization.
\item $H$ records componentwise $\hsame$ transport for $K,N,R,E,S,J,U$ and the local naming rows.
\item $C$ records displayed $\Cont$ replay from a consumer request through candidate admission, redex-frontier inspection, bounded normal comparison, subject-reduction discharge, and confluence-boundary handoff.
\item $P$ is the $\Pkg$ provenance over $\CandidateSNConfluenceBoundaryUp$, $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICRedexFrontierUp$, $\BoundedNormalEqualityCheckerUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\CandidateSNConfluenceBoundaryUp}$ row.
\end{enumerate}
The carrier compares accepted packets only by these rows. It has no coordinate for closed subject reduction, arbitrary Church--Rosser, unrestricted parallel diamond, candidate-free strong normalization, closed consistency, or a completed MetaCIC audit map.
\end{definition}

\begin{theorem}[CandidateSNConfluenceBoundary NameCert obligations]
\label{thm:candidate-sn-confluence-boundary-namecert-obligations}
For every accepted $\CandidateSNConfluenceBoundaryUp$ carrier $B=(K,N,R,E,S,J,U,H,C,P,L)$, the local $\NameCert_{\CandidateSNConfluenceBoundaryUp}$ surface consists exactly of carrier admission for the critical-path, candidate-SN, redex-frontier, bounded-checker, subject-reduction discharge, confluence-boundary, nonescape, transport, replay, provenance, and local naming rows; candidate-interface admission through $N$; redex-frontier inspection through $R$; bounded normal-equality comparison through $E$; explicit subject-reduction discharge through $S$; confluence-boundary handoff through $J$; and ledger refusal through $U$ for closed subject reduction, arbitrary Church--Rosser, unrestricted parallel diamond, candidate-free strong normalization, closed consistency, and completed audit-map closure.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:candidate-sn-confluence-boundary-carrier}. The accepted packet exposes the critical-path row, candidate strong-normalization row, redex frontier, bounded checker, subject-reduction discharge row, confluence-boundary row, nonescape row, transport, replay, provenance, and local naming row.

Candidate-mediated strong normalization is read only through $N$. This keeps the strong-normalization evidence inside the candidate interface named by the packet.

Confluence consumption then passes through the displayed redex-frontier and bounded-checker rows $R$ and $E$, followed by the discharge and boundary rows $S$ and $J$. These rows distinguish local join or normal-fragment evidence from arbitrary closed Church--Rosser.

The nonescape row $U$ and structural rows $H,C,P,L$ preserve the same finite boundary. Since no coordinate provides closed subject reduction, unrestricted parallel diamond, candidate-free strong normalization, closed consistency, or completed audit-map closure, none can be exported by the packet.
\end{proof}

\begin{theorem}[Candidate-mediated SN confluence boundary route]
\label{thm:candidate-sn-confluence-boundary-route}
Every MetaCIC consumer of an accepted $\CandidateSNConfluenceBoundaryUp$ packet factors through candidate admission, redex-frontier inspection, bounded normal-equality comparison, subject-reduction discharge, and confluence-boundary handoff before any conclusion is replayed:
$$
K \longmapsto N \longmapsto R,E \longmapsto S,J \longmapsto U \longmapsto H,C,P,L .
$$
Consequently the packet is a finite boundary witness between candidate-mediated strong normalization and confluence claims, not evidence for closed subject reduction, arbitrary Church--Rosser, candidate-free strong normalization, or closed consistency.
\end{theorem}
\begin{proof}
Start with the carrier $B=(K,N,R,E,S,J,U,H,C,P,L)$. The critical-path row $K$ locates the consumer at the MetaCIC frontier, but the first positive normalization input is still the candidate row $N$.

Any confluence-facing read must then inspect the local frontier rows $R$ and $E$. These rows expose redex cases and bounded normal comparisons only at the finite window recorded by the packet.

The discharge row $S$ and confluence-boundary row $J$ determine which subject-reduction and join inputs are actually present. The nonescape row $U$ records that all stronger endpoints remain outside the carrier.

Finally $H,C,P,L$ transport, replay, source, and name the same finite route. They do not add closed subject reduction, arbitrary Church--Rosser, candidate-free strong normalization, or closed consistency evidence.
\end{proof}

\begin{theorem}[CandidateSNConfluenceBoundary Real-phase handoff]
\label{thm:candidate-sn-confluence-boundary-real-phase-handoff}
Any Real-phase consumer using an accepted $\CandidateSNConfluenceBoundaryUp$ packet must pass through the candidate admission row $N$, redex frontier row $R$, bounded normal-equality row $E$, subject-reduction discharge row $S$, confluence-boundary row $J$, nonescape row $U$, and the L10 source faces before reaching a $\RealUp$-facing audit conclusion. The resulting handoff is the finite route
$$
K \longmapsto N \longmapsto R,E \longmapsto S,J \longmapsto U \longmapsto H,C,P,L
$$
with the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ faces read only as downstream Real and Completion source surfaces, not as closed subject reduction, arbitrary Church--Rosser, candidate-free strong normalization, or completed MetaCIC audit-map closure.
\end{theorem}
\begin{proof}
Project the carrier $B=(K,N,R,E,S,J,U,H,C,P,L)$. The only positive candidate-mediated normalization input is the admission row $N$, and the only confluence-facing local data are the redex frontier $R$ and bounded normal-equality checker $E$.

Apply \autoref{thm:candidate-sn-confluence-boundary-route}. It forces every MetaCIC consumer through $N$, then through $R,E$, and then through the subject-reduction discharge and confluence-boundary rows $S,J$ before the nonescape row $U$ is replayed.

A Real-phase audit can therefore attach the L10 source faces only after that boundary route is visible. The $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ reads are downstream source surfaces for a completion-facing audit, while $H,C,P,L$ transport, replay, source, and name the same finite route.

Because $U$ excludes closed subject reduction, arbitrary Church--Rosser, candidate-free strong normalization, and completed MetaCIC audit-map closure, the handoff does not promote the packet beyond the displayed boundary.
\end{proof}

The Lean follow-up for this packet is to provide \texttt{Nontrivial CandidateSNConfluenceBoundaryUp} and \texttt{FieldFaithful CandidateSNConfluenceBoundaryUp} instances in \texttt{TasteGate.lean}. Those instances must check that candidate admission, redex-frontier inspection, bounded equality checking, subject-reduction discharge, and confluence-boundary handoff are genuine carrier fields rather than aliases for a closed consistency endpoint.

\closureat{CandidateSNConfluenceBoundaryUp}{seedStr}

\begin{closurestatus}{\CandidateSNConfluenceBoundaryUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:candidate-sn-confluence-boundary-carrier}, \autoref{thm:candidate-sn-confluence-boundary-namecert-obligations}, \autoref{thm:candidate-sn-confluence-boundary-route}, and \autoref{thm:candidate-sn-confluence-boundary-real-phase-handoff} seed the finite MetaCIC packet separating candidate-mediated strong normalization from confluence, subject-reduction endpoints, and Real-phase audit handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, closed subject reduction, arbitrary Church--Rosser, unrestricted parallel diamond, candidate-free strong normalization, closed consistency, or completed MetaCIC audit-map closure.}
  \upgradepath{Obligation closure requires checked carrier admission, candidate-interface admission, redex-frontier inspection, bounded equality checking, subject-reduction discharge, confluence-boundary handoff, nonescape, structural transport, replay, and provenance for BEDC.Derived.CandidateSNConfluenceBoundaryUp.}
  \constructivestory{A $\CandidateSNConfluenceBoundaryUp$ packet is generated from MetaCIC critical-path rows, candidate strong-normalization evidence, redex-frontier rows, bounded normal-equality checker rows, subject-reduction discharge rows, confluence-boundary rows, nonescape data, componentwise hsame transport, displayed Cont replay, package provenance, and local NameCert evidence.}
\end{closurestatus}
