\chapter{A Concrete Naming Certificate for $\NestedIntervalDiameterZeroUp$}
\label{ch:concrete-instances-nested-interval-diameter-zero-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\NestedIntervalDiameterZeroUp$ packet records the shrinking closed interval branch of the Real and Completion route as finite BEDC certificate data. It sits after the retained-window surface of \autoref{ch:concrete-instances-nestedinterval-namecert}, the bisection discipline of \autoref{ch:concrete-instances-intervalhalving-namecert}, the constructive nested interval packet of \autoref{ch:concrete-instances-nested-interval-theorem-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The certificate names the diameter-zero descent route through displayed closed intervals; it does not import compactness, choice, quotient stream equality, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Nested interval diameter-zero carrier]
\label{def:nested-interval-diameter-zero-carrier}
A $\NestedIntervalDiameterZeroUp$ carrier is a finite $\BHist$ packet
$$
Z=(I,J,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the nested closed interval source row, read from $\NestedIntervalUp$, including closed endpoint rows, containment witnesses, and retained-window evidence.
\item $J$ is the interval-halving and descent row, read from $\IntervalHalvingUp$, recording the chosen finite bisection side, endpoint refinement, and containment descent for each inspected stage.
\item $D$ is the $\DyadicRatCoreUp$ diameter budget row recording dyadic radii, endpoint comparisons, and the finite inequality checks showing the inspected widths are below the requested tolerance.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from the nested closed interval source, halving descent, and dyadic diameter budget.
\item $E$ is the terminal $\RealUp$ seal row reached only after $I,J,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval source, halving descent, diameter budget, regular readback, Real seal, replay, provenance, and naming rows.
\item $C$ records the displayed $\Cont$ replay
$$
I,J,D \longmapsto R \longmapsto E
$$
through which Real and Completion consumers read the packet.
\item $P$ is the $\Pkg$ provenance over $\NestedIntervalDiameterZeroUp$, $\NestedIntervalUp$, $\IntervalHalvingUp$, $\NestedIntervalTheoremUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedIntervalDiameterZeroUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,J,D,R,E,H,C,P,N$. It has no coordinate for Heine--Borel compactness, open-cover compactness, a selected intersection point by choice, quotient stream equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Nested interval diameter-zero NameCert obligations]
\label{thm:nested-interval-diameter-zero-obligations}
For every accepted $\NestedIntervalDiameterZeroUp$ carrier $Z=(I,J,D,R,E,H,C,P,N)$, the local $\NameCert_{\NestedIntervalDiameterZeroUp}$ surface consists exactly of carrier admission for the displayed nine-row packet, nested closed interval source exposure through $I$, interval-halving descent exposure through $J$, dyadic diameter-budget exactness through $D$, regular rational readback through $R$, terminal Real sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, local naming through $N$, and non-escape from the excluded compactness, choice, quotient, trichotomy, and ambient-completeness principles.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:nested-interval-diameter-zero-carrier}. The rows $I,J,D,R,E,H,C,P,N$ are the whole certificate surface, so every local obligation must be read from one of those rows.

The constructive interval data are $I,J,D$. The source row $I$ supplies the closed nested intervals, $J$ records the displayed halving and descent route, and $D$ records the dyadic diameter budget that makes each requested tolerance visible as finite endpoint arithmetic.

The completion-facing read is then forced through $R$ and $E$. The regular rational row $R$ is assembled from the same nested source, descent, and diameter budget, and the Real seal $E$ is downstream of that readback.

Finally the structural rows $H,C,P,N$ transport, replay, source, and name the same packet. Since no row contains compactness, a selected point, quotient stream equality, trichotomy, or ambient completeness, the listed obligations exhaust the local NameCert.
\end{proof}

\begin{theorem}[Nested interval diameter-zero Real seal]
\label{thm:nested-interval-diameter-zero-real-seal}
Every $\RealUp$ consumer of an accepted $\NestedIntervalDiameterZeroUp$ packet factors through the finite route
$$
\NestedIntervalUp \longmapsto \IntervalHalvingUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Concretely, the consumer reads the nested closed interval source $I$, the halving descent row $J$, the dyadic diameter budget $D$, the regular rational readback $R$, and only then the Real seal $E$ with its transport, replay, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Begin with a Real-facing consumer. The only Real seal coordinate in the carrier is $E$, and the carrier places $E$ downstream of $I,J,D,R$.

The source and descent rows provide the shrinking interval data. Row $I$ exposes the nested closed interval windows, while row $J$ records the interval-halving route that preserves containment at the inspected stages.

The diameter-zero condition is read through $D$. Its dyadic budget compares widths with the requested tolerance and supplies the arithmetic needed for the $\RegSeqRatUp$ readback $R$.

The structural rows then preserve the route into $E$. Thus the Real seal is available only through the displayed finite path, and the packet cannot be repacked as Heine--Borel compactness, an open-cover argument, a choice-selected point, quotient stream equality, trichotomy, or ambient Real completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\NestedIntervalDiameterZeroUp$ Real-facing read factors through a nested closed interval source, an interval-halving descent row, a dyadic diameter budget, a RegSeqRat readback, a terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{nestedinterval, intervalhalving, nested-interval-theorem, dyadicratcore, regseqrat, real: $\NestedIntervalDiameterZeroUp$ is not bijective to any listed sibling because it binds closed interval nesting, halving descent, diameter-zero dyadic budgets, regular rational readback, Real sealing, transport, replay, provenance, and local NameCert rows into one packet.}

\closureat{NestedIntervalDiameterZeroUp}{seedStr}

\begin{closurestatus}{\NestedIntervalDiameterZeroUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-interval-diameter-zero-carrier}, \autoref{thm:nested-interval-diameter-zero-obligations}, and \autoref{thm:nested-interval-diameter-zero-real-seal} seed the finite shrinking closed interval route from nested interval source and halving descent through dyadic diameter budgets to RegSeqRat readback and Real sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Heine--Borel, open-cover compactness, a selected intersection point by choice, quotient stream equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nested closed interval exposure, interval-halving descent stability, dyadic diameter-budget exactness, RegSeqRat readback, Real-seal non-escape, transport and replay stability, provenance, and local naming for BEDC.Derived.NestedIntervalDiameterZeroUp.}
  \constructivestory{A $\NestedIntervalDiameterZeroUp$ packet is generated from a nested closed interval source row, an interval-halving descent row, a dyadic diameter budget, a RegSeqRat readback row, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
