\chapter{A Concrete Naming Certificate for $\CauchyCompletionUniversalPropertyUp$}
\label{ch:concrete-instances-cauchy-completion-universal-property-namecert}
\origin{human}

Following Bishop--Bridges and Bourbaki-style completion theory, the $\CauchyCompletionUniversalPropertyUp$ packet records the finite universal-property surface for the L10 completion interface. It sits after the metric-completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the uniform-completion route of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the functorial completion handoff of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, and the separated-metric comparison boundary of \autoref{ch:concrete-instances-separatedmetric-namecert}. The packet names the dense-source, extension, and uniqueness rows that completion consumers may cite without importing quotients, selected limits, choice, or ambient completeness.

\begin{definition}[Cauchy completion universal property carrier]
\label{def:cauchy-completion-universal-property-carrier}
A $\CauchyCompletionUniversalPropertyUp$ carrier is a finite $\BHist$ packet
$$
U=(D,K,T,F,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the dense source row, recording the source object together with the finite density witness consumed by completion readers.
\item $K$ is the completion carrier row, read through $\MetricCompletionUp$, $\UniformCompletionUp$, and $\CauchyCompletionFunctorUp$ handoff data.
\item $T$ is the complete separated target row, recording the target surface whose separatedness supports uniqueness.
\item $F$ is the source map row from $D$ into $T$ before completion is invoked.
\item $E$ is the extension map row from $K$ into $T$, tied to $F$ along the dense source row.
\item $L$ is the uniqueness classifier, comparing two extension rows over the same $D,K,T,F$ surface by separatedness rather than by quotient equality.
\item $H$ records componentwise $\hsame$ transport for $D,K,T,F,E,L$ and the local naming row.
\item $C$ records displayed $\Cont$ replay of dense-source handoff, extension existence, and uniqueness reads.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionUniversalPropertyUp$, $\MetricCompletionUp$, $\UniformCompletionUp$, $\CauchyCompletionFunctorUp$, $\SeparatedMetricUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyCompletionUniversalPropertyUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $D,K,T,F,E,L,H,C,P,N$. It has no coordinate for quotient completion, selected representatives, host limit choice, ambient real completeness, or countable choice.
\end{definition}

\begin{theorem}[CauchyCompletionUniversalProperty NameCert obligations]
\label{thm:cauchy-completion-universal-property-namecert-obligations}
For every accepted $\CauchyCompletionUniversalPropertyUp$ carrier $U=(D,K,T,F,E,L,H,C,P,N)$, the local $\NameCert_{\CauchyCompletionUniversalPropertyUp}$ surface consists exactly of five obligation rows: carrier exposure for the displayed tuple; dense-source handoff through $D$ and the source map $F$; extension existence through the completion rows $K,T,E$; uniqueness up to the classifier $L$ over the same dense-source and completion route; and ledger non-escape from choice, quotient equality, selected limits, or host limit principles.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:cauchy-completion-universal-property-carrier}. The tuple displays the dense source, completion carrier, complete separated target, source map, extension row, uniqueness classifier, transport, replay, provenance, and local naming row.

The dense-source handoff uses $D$ and $F$. A consumer must first read the source and its finite density route before it can ask for an extension into the target.

Extension existence is carried by $K,T,E$. The completion carrier is read through the metric, uniform, and functorial completion rows, while $T$ supplies the complete separated target surface. The extension row $E$ is therefore attached to displayed completion data rather than to a selected host limit.

Uniqueness is carried by $L$. Since $L$ compares extension rows over the same $D,K,T,F$ surface and uses separatedness from $T$, it does not require quotient equality or representative selection.

The ledger boundary is fixed by $H,C,P,N$. These rows transport, replay, source, and name the same displayed packet, and no excluded host-side principle appears as a coordinate of the carrier.
\end{proof}

\falsifiablePrediction{Every accepted $\CauchyCompletionUniversalPropertyUp$ consumer that exports extension existence or uniqueness while omitting the dense source, completion carrier, complete separated target, source map, extension row, uniqueness classifier, transport, replay, provenance, or local naming row refutes the packet.}

\independenceWitness{metriccompletion, uniformcompletion, cauchycompletionfunctor, separatedmetric: none is bijective because $\CauchyCompletionUniversalPropertyUp$ jointly carries dense source, completion carrier, complete separated target, source map, extension, uniqueness classifier, transport, replay, provenance, and local NameCert rows in one universal-property packet.}

\closureat{CauchyCompletionUniversalPropertyUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionUniversalPropertyUp}
  \constructivestory{A $\CauchyCompletionUniversalPropertyUp$ packet is generated from a dense source row, a completion carrier row, a complete separated target row, a source map, an extension row, a uniqueness classifier, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-universal-property-carrier} and \autoref{thm:cauchy-completion-universal-property-namecert-obligations} seed the finite L10 Cauchy completion universal-property surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, selected limits, choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, dense-source handoff, extension existence, uniqueness classification, transport replay, provenance non-escape, and TasteGate field faithfulness for BEDC.Derived.CauchyCompletionUniversalPropertyUp.}
\end{closurestatus}
