\chapter{A Concrete Naming Certificate for $\CandidateSetNormalizationUp$}
\label{ch:concrete-instances-metacic-candidate-set-normalization-namecert}
\origin{ai}

The $\CandidateSetNormalizationUp$ packet realizes the candidate-set reading of \autoref{ch:metacic-normalization-audit-map} as finite NameCert data. It records candidate evidence, closed-term projection, Pi and application adequacy, no-infinite-reduction, obstruction, transport, continuation, provenance, and local naming rows. The packet is deliberately a candidate-set surface: it does not claim unconditional strong normalization for every closed typed MetaCIC term. Its candidate-evidence and bounded-normal checking route is read through the sibling surfaces of \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert} and \autoref{ch:concrete-instances-bounded-normal-equality-checker-namecert}.

\begin{definition}[MetaCIC candidate-set normalization carrier]
\label{def:metacic-candidate-set-normalization-carrier}
A $\CandidateSetNormalizationUp$ carrier is a finite $\BHist$ packet
$$
S=(K,T,A,I,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the finite candidate-set evidence row, including candidate membership, soundness, and beta-closure evidence for the accepted read.
\item $T$ is the closed typed term projection row, recording the empty-context typed term whose normalization read is supplied by $K$.
\item $A$ is the application and Pi adequacy row, tying application reads and binder reads back to the same candidate-set evidence.
\item $I$ is the no-infinite-reduction row obtained from the candidate-set strong-normalization route.
\item $O$ is the obstruction row recording that a closed-term normalization read is refused when $K$ is absent.
\item $H$ records componentwise $\hsame$ transport for $K,T,A,I,O$ and the local naming row.
\item $C$ records displayed $\Cont$ replay from candidate-set evidence to strong normalization, closed-term projection, application and Pi adequacy, and no-infinite-reduction reads.
\item $P$ is the $\Pkg$ provenance over $\CandidateSetNormalizationUp$, $\MetaCICRedexFrontierUp$, $\MetaCICNormalizationFrontierUp$, $\BoundedNormalEqualityCheckerUp$, $\MetaCICOpenProblemLedgerUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CandidateSetNormalizationUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $K,T,A,I,O,H,C,P,N$. It contains no coordinate for evidence-free closed-term normalization, componentwise application normalization, host reduction normalization, quotient reduction equality, subject-reduction discharge, or a global normalization oracle.
\end{definition}

\begin{definition}[Candidate-set normalization frontier filter]
\label{def:candidate-set-normalization-frontier-filter}
For an accepted $\CandidateSetNormalizationUp$ carrier $S=(K,T,A,I,O,H,C,P,N)$, its public frontier filter is the finite $\BHist$ subpacket
$$
\mathsf{Frontier}(S)=(K,T,A,I,O,H,C,P,N)
$$
read in the displayed order: candidate-set evidence $K$, closed-term projection $T$, adequacy row $A$, no-infinite-reduction row $I$, obstruction row $O$, transport $H$, replay $C$, provenance $P$, and local naming $N$. A consumer reaches the redex-facing normalization frontier only through this subpacket, so the filter contains no coordinate for candidate-free strong normalization, closed subject reduction, arbitrary confluence, host conversion equality, or a global normalizer.
\end{definition}

\begin{theorem}[MetaCIC candidate-set normalization obligations]
\label{thm:metacic-candidate-set-normalization-obligations}
For every accepted $\CandidateSetNormalizationUp$ carrier $S=(K,T,A,I,O,H,C,P,N)$, the local $\NameCert_{\CandidateSetNormalizationUp}$ surface consists exactly of finite candidate-set evidence through $K$; closed-term projection through $T$; application and Pi adequacy through $A$; no-infinite-reduction through $I$; obstruction when the candidate-set row is absent through $O$; componentwise transport through $H$; displayed replay through $C$; provenance through $P$; local naming through $N$; and non-escape from unconditional MetaCIC strong normalization.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:metacic-candidate-set-normalization-carrier}. The tuple displays the candidate-set evidence, closed typed term projection, adequacy row, no-infinite-reduction row, obstruction row, transport, replay, provenance, and local name.

The positive route begins at $K$. Candidate-set membership, soundness, and beta-closure are read before $T$, $A$, or $I$ can export a normalization-facing conclusion.

The closed-term projection is $T$, and the application and Pi adequacy route is $A$. Both rows consume the same candidate-set evidence rather than a componentwise strong-normalization shortcut.

The no-infinite-reduction row $I$ is downstream of that evidence. If $K$ is absent, $O$ records the obstruction, so the packet refuses an evidence-free theorem over all closed typed terms.

Finally $H,C,P,N$ transport, replay, source, and name the same finite branch. Since no global normalization oracle or quotient reduction equality is present in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Candidate-set normalization redex non-escape]
\label{thm:candidate-set-normalization-redex-nonescape}
Every redex-frontier consumer of an accepted $\CandidateSetNormalizationUp$ carrier must pass through the frontier filter $K,T,A,I,O,H,C,P,N$ of \autoref{def:candidate-set-normalization-frontier-filter}. It exports no candidate-free strong normalization, no closed subject-reduction theorem, and no arbitrary confluence principle.
\end{theorem}
\begin{proof}
Project the accepted carrier and then read its frontier filter. The first row is $K$, so the consumer starts from candidate-set evidence rather than from a redex-normalization oracle.

The closed-term row $T$ and adequacy row $A$ are downstream of the same candidate evidence. They can expose closed projection and application or Pi adequacy only through that evidence.

The no-infinite-reduction row $I$ and obstruction row $O$ complete the normalization-facing branch. If the candidate evidence is absent, $O$ records refusal instead of supplying a candidate-free theorem.

Finally $H,C,P,N$ transport, replay, source, and name the same branch. Since the filter has no subject-reduction, confluence, or global-normalizer coordinate, no consumer can export those conclusions from this packet.
\end{proof}

\begin{theorem}[Candidate-set normalization candidate-closed handoff]
\label{thm:candidate-set-normalization-candidate-closed-handoff}
For every accepted $\CandidateSetNormalizationUp$ carrier, the handoff from candidate-set evidence to the closed-term projection remains mediated by $K,T,A,I,O,H,C,P,N$. In particular, the closed projection row $T$ is not a candidate-free closed normalization theorem and cannot be reused without the candidate-set evidence row $K$.
\end{theorem}
\begin{proof}
Read the carrier as $S=(K,T,A,I,O,H,C,P,N)$. The closed-term projection row is named as $T$, but its admissibility is part of the same finite packet as $K$.

The adequacy and no-infinite-reduction rows $A$ and $I$ also consume the candidate-set route. They do not create a detached closed-term theorem, because the obstruction row $O$ records refusal when $K$ is absent.

Transport and replay through $H$ and $C$, with provenance and naming through $P$ and $N$, preserve the same candidate-mediated route. Thus the closed projection remains a handoff inside the frontier filter rather than a standalone normalization principle.
\end{proof}

\begin{theorem}[MetaCIC candidate-set normalization idempotence]
\label{thm:metacic-candidate-set-normalization-idempotence}
Let $S=(K,T,A,I,O,H,C,P,N)$ be an accepted $\CandidateSetNormalizationUp$ carrier whose candidate-set packet has already been normalized through the displayed frontier-dependency rows. Applying the same normalization route again exposes the same accepted candidate rows, the same closed-term projection, the same application and Pi adequacy rows, and no additional spectral-trigger row.
\end{theorem}
\begin{proof}
Use the carrier and obligation surface of \autoref{def:metacic-candidate-set-normalization-carrier} and \autoref{thm:metacic-candidate-set-normalization-obligations}. The first normalization pass can read only $K,T,A,I,O,H,C,P,N$, and the accepted candidate-set evidence is already attached to the displayed no-infinite-reduction and obstruction rows.

The frontier-dependency rows of \autoref{ch:concrete-instances-metacic-frontier-dependency-matrix-namecert} determine which candidate rows may be exposed before the closed-term projection and adequacy rows are replayed. Running the same route again therefore reuses the same dependency rows rather than introducing a new candidate branch.

Finally compare with the spectral-trigger surface of \autoref{ch:concrete-instances-wobble-quotient-spectral-trigger-namecert}. A trigger row would have to be present as an additional obstruction or replay coordinate, but the $\CandidateSetNormalizationUp$ classifier contains no such coordinate beyond $O$ and $C$. The second pass is therefore idempotent on accepted candidate rows and creates no further spectral-trigger row.
\end{proof}

The Lean-side TasteGate surface for this packet requires future $\mathsf{Nontrivial}\ \CandidateSetNormalizationUp$ and $\mathsf{FieldFaithful}\ \CandidateSetNormalizationUp$ instances in \texttt{lean4/BEDC/Derived/CandidateSetNormalizationUp/TasteGate.lean}. Those instances must distinguish candidate-set evidence, closed-term projection, adequacy, no-infinite-reduction, obstruction, transport, replay, provenance, and local naming as separate fields.

\falsifiablePrediction{No accepted closed-term strong-normalization read through $\CandidateSetNormalizationUp$ bypasses candidate evidence or candidate-set evidence.}

\independenceWitness{metacicredexfrontier, metacicnormalizationfrontier, bounded-normal-equality-checker, metacicopenproblemledger: none is bijective because $\CandidateSetNormalizationUp$ jointly carries candidate-set evidence, closed-term projection, application and Pi adequacy, no-infinite-reduction, obstruction, transport, replay, provenance, and local NameCert rows.}

\closureat{CandidateSetNormalizationUp}{seedStr}

\begin{closurestatus}{\CandidateSetNormalizationUp}
  \constructivestory{A $\CandidateSetNormalizationUp$ packet is generated from finite candidate-set evidence, a closed typed term projection, application and Pi adequacy, a no-infinite-reduction row, an obstruction row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-candidate-set-normalization-carrier} and \autoref{thm:metacic-candidate-set-normalization-obligations} seed the finite candidate-set normalization surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim unconditional MetaCIC strong normalization, evidence-free application normalization, subject reduction, host normalization, quotient reduction equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked candidate-set evidence, closed-term projection, application and Pi adequacy, no-infinite-reduction, obstruction exactness, transport replay, and TasteGate field faithfulness for BEDC.Derived.CandidateSetNormalizationUp.}
\end{closurestatus}
