\chapter{A Concrete Naming Certificate for $\NestedClosedIntervalUp$}
\label{ch:concrete-instances-nested-closed-interval-namecert}
\origin{human}

Following Cantor's nested interval argument and Bishop-style constructive interval reasoning, the $\NestedClosedIntervalUp$ packet records the finite BEDC carrier surface for a descending family of closed located intervals. It is the interval-side seed used by completion arguments before any point-selection, quotient completion, or ambient completeness principle is introduced. The construction consumes the located endpoint rows of \autoref{ch:concrete-instances-locatedinterval-namecert}, the nested-existence route of \autoref{ch:concrete-instances-cantor-completeness-namecert}, the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name handoff of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[Nested closed interval carrier]
\label{def:nested-closed-interval-carrier}
A $\NestedClosedIntervalUp$ carrier is a finite $\BHist$ packet
$$
K=(I,D,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the retained $\LocatedIntervalUp$ row family, listing the inspected closed intervals, endpoint order checks, containment witnesses, and nonempty endpoint certificates;
\item $D$ is the $\DyadicRatCoreUp$ ledger for endpoint comparisons, width estimates, and diameter-to-tolerance requests;
\item $S$ is the $\StreamNameUp$ finite-window schedule used to request lower and upper endpoint observations;
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same interval windows and dyadic tolerance ledger;
\item $E$ is the $\RealUp$ handoff row exposed only after the displayed nested interval, dyadic, stream, and regular rational rows are present;
\item $H$ stores componentwise $\hsame$ transport for $I,D,S,R,E$ and the structural naming rows;
\item $C$ stores the finite $\Cont$ replay from nested closed interval rows through dyadic tolerance control, stream windows, regular readback, and Real handoff;
\item $P$ is the $\Pkg$ provenance over $\NestedClosedIntervalUp$, $\LocatedIntervalUp$, $\CantorCompletenessUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\NestedClosedIntervalUp}$ row.
\end{enumerate}
The carrier exports only these finite rows. It contains no selected intersection point, quotient-real representative, countable-choice operator, open-cover compactness principle, or ambient complete-real object.
\end{definition}

\begin{theorem}[Nested closed interval seed boundary]
\label{thm:nested-closed-interval-seed-boundary}
For every accepted $\NestedClosedIntervalUp$ carrier $K=(I,D,S,R,E,H,C,P,N)$, every completion-facing consumer of the packet reads first through the $\LocatedIntervalUp$ row family $I$, then through the $\DyadicRatCoreUp$ ledger $D$, the $\StreamNameUp$ schedule $S$, the $\RegSeqRatUp$ readback $R$, and only then the $\RealUp$ handoff $E$ with structural rows $H,C,P,N$ for $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Consequently the packet supplies a nested closed interval carrier surface for the current L10 completion path without claiming an intersection selector, a quotient completion, or an ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:nested-closed-interval-carrier}. The interval row family $I$ is the only source coordinate for closed interval data, and it already records the inspected endpoint order, containment, and nonempty rows.

The completion-facing route is then finite. The dyadic row $D$ supplies endpoint and width comparisons, the stream row $S$ names the requested endpoint windows, and the regular rational row $R$ packages the same retained windows as readback data.

The Real-facing handoff is downstream of those rows. Since $E$ is visible only after $I,D,S,R$, and since $H,C,P,N$ merely transport, replay, source, and name the same packet, no excluded selector, quotient, compactness, choice, or ambient completeness coordinate can be read from the carrier.
\end{proof}

\closureat{NestedClosedIntervalUp}{seedStr}

\begin{closurestatus}{\NestedClosedIntervalUp}
  \constructivestory{A $\NestedClosedIntervalUp$ packet is generated from retained located closed interval rows, dyadic endpoint and width ledgers, StreamName finite windows, RegSeqRat readback, Real handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-closed-interval-carrier} and \autoref{thm:nested-closed-interval-seed-boundary} seed the finite nested closed interval carrier route consumed by Cantor completeness and Real completion arguments.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.NestedClosedIntervalUp}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close selected intersection points, quotient completions, ambient complete uniform spaces, open-cover compactness, countable choice, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nested interval exposure, dyadic endpoint and width exactness, StreamName window exposure, RegSeqRat readback, Real handoff nonescape, transport, replay, provenance, and local naming for BEDC.Derived.NestedClosedIntervalUp.}
\end{closurestatus}
