\chapter{A Concrete Naming Certificate for $\BishopCauchyRealUp$}
\label{ch:concrete-instances-bishopcauchyreal-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopCauchyRealUp$ packet records a modulus-equipped Cauchy real presentation as finite BEDC certificate data before the open Real and Completion route reads the terminal seal. It sits after the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the modulus discipline of \autoref{ch:concrete-instances-cauchymodulus-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names the constructive presentation of real data by displayed Cauchy approximants and explicit moduli; it does not make $\RealUp$ a quotient carrier, assert ambient completeness, choose a representative limit, or import countable choice.

\begin{definition}[Bishop Cauchy real carrier]
\label{def:bishop-cauchy-real-carrier}
A $\BishopCauchyRealUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,M,S,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\RegSeqRatUp$ regular rational source row that supplies the rational approximants read by the packet.
\item $M$ is the $\CauchyModulusUp$ row that records the finite tolerance-to-stage ledger used to inspect $Q$.
\item $S$ is the $\StreamNameUp$ finite-window schedule through which a consumer asks for approximation data.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and arithmetic row used to compare requested precisions with the displayed rational approximants.
\item $R$ is the terminal $\RealUp$ seal reached only after $Q,M,S,D$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the regular source, modulus, stream schedule, dyadic ledger, real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay of the route
$$
Q,M,S,D \longmapsto R \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\BishopCauchyRealUp$, $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BishopCauchyRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,M,S,D,R,H,C,P,N$. It has no coordinate for quotient equality of Cauchy streams, selected host limits, ambient $\RealUp$ completeness, trichotomy, or countable choice.
\end{definition}

\begin{theorem}[Bishop Cauchy real NameCert obligations]
\label{thm:bishop-cauchy-real-namecert-obligations}
For every accepted $\BishopCauchyRealUp$ carrier $B=(Q,M,S,D,R,H,C,P,N)$, the local $\NameCert_{\BishopCauchyRealUp}$ surface consists exactly of carrier admission, regular rational source exposure through $Q$, explicit Cauchy modulus exposure through $M$, finite stream-window routing through $S$, dyadic tolerance comparison through $D$, terminal real sealing through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, local naming through $N$, and non-escape from quotient stream equality, selected representatives, host limit equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:bishop-cauchy-real-carrier}. The accepted packet exposes exactly the regular rational source row, the modulus row, the stream-window schedule, the dyadic tolerance ledger, the real seal, and the structural rows.

The Cauchy presentation is read through $Q,M,S,D$. The $\RegSeqRatUp$ row supplies regular rational approximants, the $\CauchyModulusUp$ row supplies the displayed tolerance-to-stage ledger, $\StreamNameUp$ bounds each read to finite windows, and $\DyadicRatCoreUp$ supplies the tolerance arithmetic.

Only after those rows are visible does the terminal $\RealUp$ seal $R$ appear. Transport, replay, provenance, and naming preserve the same route through $H,C,P,N$. Since the excluded completion principles are absent from the carrier, the listed rows exhaust the local $\NameCert$ surface.
\end{proof}

\begin{theorem}[Bishop Cauchy real RegSeqRat handoff]
\label{thm:bishop-cauchy-real-regseqrat-handoff}
Every regular-rational read of an accepted $\BishopCauchyRealUp$ packet factors through
$$
\RegSeqRatUp,\ \CauchyModulusUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RealUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Thus a Real-facing consumer receives a modulus-controlled regular Cauchy presentation rather than a quotient Cauchy class, a chosen representative, a host limit, or a completeness principle.
\end{theorem}
\begin{proof}
Start with the displayed carrier $B=(Q,M,S,D,R,H,C,P,N)$. The source row $Q$ is the only regular rational source available to the classifier.

The read cannot bypass $M,S,D$. The modulus row records which finite stages answer a requested tolerance, the stream row restricts the answer to visible windows, and the dyadic row records the endpoint arithmetic used by the tolerance comparison.

The seal row $R$ is downstream of that route. The structural rows then transport, replay, source, and name the same packet, so every exported regular-rational read has the stated factorization and no hidden completion coordinate.
\end{proof}

\begin{theorem}[Bishop Cauchy real regular readback seal]
\label{thm:bishop-cauchy-real-regular-readback-seal}
Any $\RealUp$-facing seal read from an accepted $\BishopCauchyRealUp$ carrier $B=(Q,M,S,D,R,H,C,P,N)$ must first expose the $\RegSeqRatUp$ source row $Q$, the $\CauchyModulusUp$ ledger $M$, the $\StreamNameUp$ finite window $S$, and the $\DyadicRatCoreUp$ tolerance row $D$. The terminal seal $R$ may then be read only as the endpoint of the displayed route
$$
Q,M,S,D \longmapsto R \longmapsto H,C,P,N .
$$
Thus a Real-facing consumer receives the regular-readback-to-seal dependency as finite BEDC data, not as a quotient completion, a chosen representative, a host limit equality, or an ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:bishop-cauchy-real-carrier}. The rows $Q,M,S,D$ precede the terminal seal $R$ and are the only displayed source, modulus, window, and tolerance coordinates available to a Real-facing read.

Apply the obligation surface of \autoref{thm:bishop-cauchy-real-namecert-obligations}. It identifies carrier admission, source exposure, modulus exposure, stream-window routing, dyadic comparison, terminal sealing, transport, replay, provenance, and local naming as the complete local NameCert surface.

Finally use the RegSeqRat handoff of \autoref{thm:bishop-cauchy-real-regseqrat-handoff}. It forces every regular-rational read through the same $Q,M,S,D,R,H,C,P,N$ route, so the $\RealUp$ seal is terminal for that route and cannot hide quotient completion or host real equality.
\end{proof}

\begin{theorem}[Bishop Cauchy real seal boundary]
\label{thm:bishop-cauchy-real-real-seal-boundary}
The $\RealUp$ seal of an accepted $\BishopCauchyRealUp$ carrier is public only as the endpoint of the displayed route
$$
Q,M,S,D \longmapsto R .
$$
Consequently the packet exposes a constructive real presentation for the open Real and Completion route while leaving quotient completion, ambient real completeness, selected limits, host real equality, trichotomy, and countable choice outside the exported surface.
\end{theorem}
\begin{proof}
Inspect the carrier order. The terminal seal $R$ is stored after the regular source, modulus, stream-window, and dyadic tolerance rows.

The continuation row $C$ replays that order for consumers. A Real-facing read therefore must display the regular rational approximants, the modulus ledger, the finite observation window, and the dyadic tolerance comparison before the seal can be consumed.

The remaining structural rows $H,P,N$ preserve and name the same boundary. Since no quotient, selected limit, host equality, trichotomy, choice, or ambient completeness coordinate occurs in the packet, the seal is exactly the displayed endpoint of the constructive Cauchy presentation.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopCauchyRealUp$ real-facing read factors through a displayed $\RegSeqRatUp$ source, $\CauchyModulusUp$ ledger, $\StreamNameUp$ finite window, $\DyadicRatCoreUp$ tolerance row, terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{regseqrat, cauchymodulus, streamname, dyadicratcore, real: $\BishopCauchyRealUp$ is not bijective to any listed sibling because it binds a modulus-controlled Cauchy real presentation, finite observation windows, dyadic tolerance arithmetic, terminal real sealing, transport, replay, provenance, and local NameCert rows into one packet.}

\closureat{BishopCauchyRealUp}{seedStr}

\begin{closurestatus}{\BishopCauchyRealUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-cauchy-real-carrier}, \autoref{thm:bishop-cauchy-real-namecert-obligations}, \autoref{thm:bishop-cauchy-real-regseqrat-handoff}, and \autoref{thm:bishop-cauchy-real-real-seal-boundary} seed the modulus-equipped Cauchy real presentation surface for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, ambient $\RealUp$ completeness, selected limits, host real equality, trichotomy, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus-controlled regular source exposure, finite stream-window routing, dyadic tolerance readback, real-seal boundary, transport and replay stability, provenance non-escape, and TasteGate field faithfulness for BEDC.Derived.BishopCauchyRealUp.}
  \constructivestory{A $\BishopCauchyRealUp$ packet is generated from a regular rational source, an explicit Cauchy modulus, finite stream windows, dyadic tolerance rows, a terminal Real seal, componentwise transport, displayed replay, package provenance, and a local NameCert row.}
\end{closurestatus}
