\chapter{A Concrete Naming Certificate for $\CoreStateGraphUp$}
\label{ch:concrete-instances-core-state-graph-namecert}
\origin{ai}

The $\CoreStateGraphUp$ packet realizes the strict partial-aware core-state graph of \autoref{def:philosophy-strict-core-state-graph} as finite NameCert data. It records the $22$ state rows, the single-coordinate edge ledger, the $9$ component ledger, observed module-generator rows, transport, replay, provenance, and local naming surface used by the DNA-window boundary analysis. The packet is a finite graph-state ledger for accepted reads, not a mechanistic evolutionary model, not a hidden distance oracle, and not a collapse of ambiguous table rows.

\begin{definition}[Core state graph carrier]
\label{def:core-state-graph-carrier}
A $\CoreStateGraphUp$ carrier is a finite $\BHist$ packet
$$
G=(V,E,K,M,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $V$ is the vertex ledger of the $22$ partial-aware core states, retaining ambiguous rows as separate labels.
\item $E$ is the strict edge ledger, adding an edge exactly when two state vectors differ in one core coordinate.
\item $K$ is the component ledger with $9$ connected components and the displayed component-size row.
\item $M$ is the observed module-generator row for UGA, UAA/UAG, AGR, AUA, and AAA support moves.
\item $T$ is the table-group provenance row tying vertices and components to the comparison-family table identifiers.
\item $H$ records componentwise $\hsame$ transport for $V,E,K,M,T$ and the local naming row.
\item $C$ records displayed $\Cont$ replay of accepted graph reads through vertex, edge, component, module-generator, and table-group rows.
\item $P$ is the $\Pkg$ provenance over $\CoreStateGraphUp$, the originating DNA-window strict graph vision, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CoreStateGraphUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $V,E,K,M,T,H,C,P,N$. It has no coordinate for collapsed ambiguous rows, unlisted graph edges, a connectedness assertion, a hidden biological mechanism, or a host-side graph oracle.
\end{definition}

\begin{theorem}[Core state graph NameCert obligations]
\label{thm:core-state-graph-namecert-obligations}
For every accepted $\CoreStateGraphUp$ carrier $G=(V,E,K,M,T,H,C,P,N)$, the local $\NameCert_{\CoreStateGraphUp}$ surface consists exactly of vertex-ledger exposure, strict edge-ledger exposure, component-ledger exposure, module-generator exposure, table-group provenance, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, local naming, and non-escape from collapsed ambiguity, unlisted edges, hidden mechanisms, connectedness import, and host-side graph computation.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:core-state-graph-carrier}. The finite graph data are exactly the vertex row $V$, edge row $E$, component row $K$, module-generator row $M$, and table-group row $T$.

The strict graph read of \autoref{def:philosophy-strict-core-state-graph} is recovered by reading $V$ before $E$, then reading $K$ as the component ledger generated from that edge relation. The module-generator row $M$ is separate from the strict edge row and therefore cannot add hidden edges.

Transport, replay, provenance, and local naming are supplied by $H,C,P,N$. Since no other coordinate appears in the carrier, accepted reads cannot collapse ambiguous states, import a connectedness theorem, or consult a host graph oracle.
\end{proof}

\begin{theorem}[Core state graph finite acceptance route]
\label{thm:core-state-graph-finite-acceptance-route}
Every accepted $\CoreStateGraphUp$ read factors through the finite route
$$
V,E,K,M,T \longmapsto H,C,P,N .
$$
Thus the read preserves the $22$-state ledger, the strict edge ledger, the $9$-component ledger, and the module-generator row as separate displayed coordinates.
\end{theorem}
\begin{proof}
Begin with the carrier projection. The graph-facing rows $V,E,K$ specify the partial-aware state space, strict adjacency relation, and connected-component ledger.

Next read $M$ and $T$. These rows record module-generator support and table-group provenance, but neither row rewrites the strict edge relation. The structural rows $H,C,P,N$ then transport, replay, source, and name only the same finite coordinates.

The route is therefore exhausted by the displayed packet. A consumer that removes any one of $V,E,K,M,T$ loses a named graph or provenance coordinate, so no accepted read can factor through a smaller hidden graph.
\end{proof}

\falsifiablePrediction{Every accepted read of the strict core-state graph factors through the $22$-state ledger, strict edge ledger, $9$-component ledger, module-generator row, table-group provenance, transport, replay, provenance, and local naming rows.}

\independenceWitness{Nearby finite graph and state-ledger siblings: codon-transition-matrix, dna-four-phase-alphabet-bridge, finite-observation-fold, and finite-observation-confluence. The $\CoreStateGraphUp$ packet is not bijective to any one sibling because it carries the partial-aware vertex ledger, strict edge ledger, component ledger, module-generator support, and table-group provenance simultaneously.}

Later Lean work should place $\mathrm{Nontrivial}\ \CoreStateGraphUp$ and $\mathrm{FieldFaithful}\ \CoreStateGraphUp$ instances in the TasteGate surface. Nontriviality must distinguish carriers with the same vertex ledger but different strict edge or component rows, while field faithfulness must preserve $V,E,K,M,T,H,C,P,N$ separately.

\closureat{CoreStateGraphUp}{seedStr}

\begin{closurestatus}{\CoreStateGraphUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:core-state-graph-carrier}, \autoref{thm:core-state-graph-namecert-obligations}, and \autoref{thm:core-state-graph-finite-acceptance-route} seed the finite strict graph surface over state, edge, component, module-generator, table-group, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a mechanistic evolutionary model, graph connectedness, hidden distance computation, collapsed ambiguous table rows, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, strict edge exposure, component-ledger exposure, module-generator separation, finite route exactness, and TasteGate field faithfulness for BEDC.Derived.CoreStateGraphUp.}
  \constructivestory{A $\CoreStateGraphUp$ packet is generated from a partial-aware vertex ledger, strict edge ledger, component ledger, module-generator support row, table-group provenance, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
