\chapter{A Concrete Naming Certificate for $\PositiveConeUp$}
\label{ch:concrete-instances-positive-cone-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\PositiveConeUp$
packet isolates the positive cone over $\RealUp$ as finite
apartness-from-zero data with algebra-facing closure rows. It refines the
$\PositiveRealUp$ carrier of
\autoref{ch:concrete-instances-positivereal-namecert}, the
$\ApartnessRealUp$ separation surface of
\autoref{ch:concrete-instances-apartnessreal-namecert}, the
$\LocatedApartnessUp$ route of
\autoref{ch:concrete-instances-located-apartness-namecert}, and the
finite-name substrates $\DyadicRatCoreUp$, $\RegSeqRatUp$, and
$\StreamNameUp$ used by \autoref{ch:concrete-instances-real-namecert}.

\section{Carrier and cone packet}
\label{sec:positive-cone-carrier}

\begin{definition}[PositiveCone carrier]
\label{def:positive-cone-carrier}
A $\PositiveConeUp$ carrier is a finite packet
$(R,P,A,D,W,Q,H,C,K,N)$ with the following displayed rows:
\begin{enumerate}
\item $R$, a sealed $\RealUp$ row for the real name whose cone membership is
being classified;
\item $P$, a $\PositiveRealUp$ row naming the same real through finite
positivity evidence;
\item $A$, an $\ApartnessRealUp$ apartness-to-zero row whose left endpoint is
the zero real row and whose right endpoint is $R$;
\item $D$, a positive $\DyadicRatCoreUp$ radius ledger consumed by $A$ and $P$;
\item $W$, a finite $\StreamNameUp$ observation window shared by the zero row,
the real row, and the positivity packet;
\item $Q$, a $\RegSeqRatUp$ readback row for the scheduled rational
observations of $R$ on $W$;
\item $H$, the componentwise $\hsame$ rows for the real seal, positivity row,
apartness row, radius ledger, window, and readback;
\item $C$, the displayed $\Cont$ replay routes keeping the finite observations
attached to the transported packet;
\item $K$, the $\mathsf{Pkg}$ provenance rows for the real seal, positive-real
row, apartness ledger, dyadic radius, stream window, regular-rational
readback, and replay surface;
\item $N$, the local $\NameCert$ row binding these nine rows as one positive
cone certificate.
\end{enumerate}
The carrier contains no order decision coordinate, no quotient stream equality,
no selected limit, and no ambient completeness witness. Cone membership is the
finite compatibility of the displayed real, positive-real, apartness, radius,
window, readback, transport, continuation, provenance, and local certificate
rows.
\end{definition}

\section{NameCert obligations}
\label{sec:positive-cone-namecert-obligations}

\begin{theorem}[PositiveCone NameCert obligations]
\label{thm:positive-cone-namecert-obligations}
The local $\NameCert_{\PositiveConeUp}$ surface for the carrier of
\autoref{def:positive-cone-carrier} consists of six finite obligations:
\begin{enumerate}
\item carrier admission: the displayed rows $(R,P,A,D,W,Q,H,C,K,N)$ occur in
one finite $\mathsf{BHist}$ packet;
\item classifier transport: accepted cone carriers compare only by
componentwise transport of the real seal, positive-real row, apartness row,
radius ledger, finite window, readback, replay, provenance, and local
certificate rows;
\item zero-exclusion: the apartness-to-zero row $A$ and the positive-real row
$P$ share the same sealed real endpoint $R$ and the same finite observation
window $W$;
\item positive-radius exactness: the positive dyadic radius used by the
apartness row and by the positive-real row is exactly the displayed
$\DyadicRatCoreUp$ ledger $D$;
\item addition and multiplication closure surface: algebra consumers receive
only the finite cone rows required to transport positivity across displayed
addition-facing and multiplication-facing packet reads;
\item ledger non-escape: downstream consumers can inspect only the ten carrier
rows and their $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ witnesses.
\end{enumerate}
These obligations certify the positive cone as a finite NameCert packet over
the real-name substrate. They do not certify trichotomy, a host total order,
quotient equality of streams, selected limits, or ambient real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:positive-cone-carrier}. The projection
exposes the sealed real row, the positive-real row, the apartness-to-zero row,
the positive dyadic radius, the finite observation window, the
regular-rational readback, transport, replay, provenance, and local
certificate rows.

Carrier admission and classifier transport are componentwise. The $\hsame$ and
$\Cont$ rows keep the real seal, positive-real packet, apartness packet, radius
ledger, stream window, and readback attached to the same finite observation
surface after transport.

Zero-exclusion and positive-radius exactness are read from the shared rows.
The apartness endpoint and the positive-real carrier both name $R$, while $D$
is the only positive dyadic radius ledger available to either positivity read.

The closure surface is therefore only a ledger interface for later algebraic
consumers. Since the packet contains no coordinate for order decisions,
quotient representatives, chosen limits, or completeness witnesses, every
consumer remains confined to the displayed finite evidence.
\end{proof}

\begin{theorem}[PositiveCone apartness-order handoff]
\label{thm:positive-cone-apartness-order-handoff}
Every accepted $\PositiveConeUp$ read factors through the displayed
$\PositiveRealUp$, $\ApartnessRealUp$, and $\LocatedApartnessUp$ rows, together
with the $\DyadicRatCoreUp$ radius ledger, $\StreamNameUp$ finite window, and
$\RegSeqRatUp$ readback of \autoref{def:positive-cone-carrier}. Consequently a
later order, metric-radius, or real-algebra consumer receives cone membership
only as finite apartness-radius evidence with visible $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$ provenance.

No accepted read exports trichotomy, host order, quotient stream equality,
selected limits, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted cone carrier and project its positive-real coordinate
$P$. By \autoref{def:positive-cone-carrier}, $P$ shares the real endpoint $R$,
the radius ledger $D$, the finite window $W$, and the readback row $Q$ with the
apartness-to-zero coordinate $A$.

Read the packet through the surrounding siblings. The $\PositiveRealUp$ row
supplies positivity as apartness from zero, the $\ApartnessRealUp$ row exposes
the finite separation packet, and the $\LocatedApartnessUp$ route supplies the
located handoff used by downstream metric-radius consumers.

Transport is again componentwise. The $\hsame$, $\Cont$, $\mathsf{Pkg}$, and
$\NameCert$ rows move the positive-real, apartness, radius, window, and
readback coordinates together, so every transported read still factors through
the displayed finite surfaces.

The carrier has no row for totality, trichotomy, quotient equality, selected
limits, or real completeness. Therefore the handoff is an order-facing
interface only through finite apartness-radius evidence.
\end{proof}

\closureat{PositiveConeUp}{seedStr}

\begin{closurestatus}{\PositiveConeUp}
  \constructivestory{A $\PositiveConeUp$ packet is generated from a sealed real row, a positive-real row, an apartness-to-zero row, one positive dyadic radius ledger, one finite observation window, one regular-rational readback, transport, replay, provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:positive-cone-carrier}, \autoref{thm:positive-cone-namecert-obligations}, and \autoref{thm:positive-cone-apartness-order-handoff} name the seed carrier, obligation surface, and finite apartness-order handoff for positive cone packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim trichotomy of constructive reals, a host total order, quotient stream equality, selected limits, ambient real completeness, or a standard bridge.}
  \upgradepath{To reach obligationClosure, the carrier, six obligation rows, and apartness-order handoff must be checked as finite BEDC packet obligations.}
\end{closurestatus}
