\chapter{A Concrete Naming Certificate for $\MedianLeakageSpectrumUp$}
\label{ch:concrete-instances-median-leakage-spectrum-namecert}
\origin{ai}

The $\MedianLeakageSpectrumUp$ packet realizes the active median leakage table of \autoref{def:philosophy-active-median-leakage} and the direct leakage spectrum of \autoref{thm:philosophy-direct-leakage-spectrum} as finite BEDC NameCert data. It consumes the six-coordinate source window of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the finite codon transition vocabulary of \autoref{ch:concrete-instances-codon-transition-matrix-namecert}, the stabilization boundary of \autoref{ch:concrete-instances-spectral-stabilization-namecert}, the conditioned survival-chain route of \autoref{ch:concrete-instances-doob-survival-chain-namecert}, and the host-primitive refusal surface of \autoref{ch:concrete-instances-hostprimitiveleakage-namecert}. The packet names a finite leakage spectrum; it does not identify median closure with biological translation identity, choose a stochastic model, or import host primitive enumeration.

\begin{definition}[MedianLeakageSpectrum carrier]\label{def:median-leakage-spectrum-carrier}
A $\MedianLeakageSpectrumUp$ carrier is a finite $\BHist$ packet
$$
L=(W,T,A,M,I,G,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ source-window row exposing the finite six-bit codon carrier and coordinatewise median readback.
\item $T$ is the $\CodonTransitionMatrixUp$ transition-vocabulary row naming the finite scan, elongate, terminate, readthrough, repair, and mutate states available to the consumer.
\item $A$ is the active-triple row, recording the $286$ distinct active triples and the closed versus leaking split $264+22$.
\item $M$ is the median-output row, recording the coordinatewise majority output attached to each active triple.
\item $I$ is the inactive-output row, listing the six direct inactive outputs $\mathrm{UUG}$, $\mathrm{AAG}$, $\mathrm{UGG}$, $\mathrm{ACA}$, $\mathrm{AUG}$, and $\mathrm{UCG}$.
\item $G$ is the centrality ledger, recording the median centrality counts for active and inactive outputs together with the direct leakage multiplicities.
\item $D$ is the direct-output multiplicity row, recording the displayed multiplicities $8,4,4,2,2,2$ for the six inactive outputs.
\item $H$ records componentwise $\hsame$ transport for the source window, transition vocabulary, active triples, median outputs, inactive outputs, centrality ledger, direct multiplicities, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a leakage request through $W,T,A,M,I,G,D$ in that order.
\item $P$ is the $\Pkg$ provenance over $\MedianLeakageSpectrumUp$, $\CodonSixBitWindowUp$, $\CodonTransitionMatrixUp$, $\SpectralStabilizationUp$, $\DoobSurvivalChainUp$, $\HostPrimitiveLeakageUp$, \autoref{def:philosophy-active-median-leakage}, \autoref{thm:philosophy-direct-leakage-spectrum}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MedianLeakageSpectrumUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $W,T,A,M,I,G,D,H,C,P,N$. It has no coordinate for host primitive enumeration, biological translation identity, stochastic model selection, quotient codon equality, or an unrecorded median table.
\end{definition}

\begin{theorem}[MedianLeakageSpectrum NameCert obligations]\label{thm:median-leakage-spectrum-namecert-obligations}
For every accepted $\MedianLeakageSpectrumUp$ carrier $L=(W,T,A,M,I,G,D,H,C,P,N)$, the local $\NameCert_{\MedianLeakageSpectrumUp}$ surface consists exactly of carrier admission for the codon source window, transition vocabulary, active-triple row, median-output row, inactive-output row, centrality ledger, direct-output multiplicity row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every leakage multiplicity read must expose $A,M,I,G,D$ over the same $W,T$ source before any downstream spectral, survival-chain, or host-primitive refusal consumer may inspect it. No median-leakage obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:median-leakage-spectrum-carrier}. The tuple displays the source window, transition vocabulary, active triples, median outputs, inactive outputs, centrality counts, direct multiplicities, transport, replay, provenance, and local naming rows.

The spectrum route is ordered. A consumer first reads $W,T$, then the active-triple ledger $A$, then the median-output row $M$, then the inactive-output row $I$, and then the centrality and multiplicity rows $G,D$.

The downstream dependencies are consequently consumers rather than hidden data. $\SpectralStabilizationUp$ and $\DoobSurvivalChainUp$ may read the displayed spectrum only after the finite leakage rows are present, while $\HostPrimitiveLeakageUp$ records that no host primitive enumeration may replace them.

Finally, $H,C,P,N$ preserve, replay, source, and name the same finite route. Since the carrier has no coordinate for biological translation identity, stochastic model selection, quotient codon equality, host primitive enumeration, or an unrecorded median table, the refusal clause is exhausted by the carrier inventory.
\end{proof}

\begin{theorem}[MedianLeakageSpectrum direct output route]\label{thm:median-leakage-spectrum-direct-output-route}
Every accepted $\MedianLeakageSpectrumUp$ direct-output read factors through
$$
\CodonSixBitWindowUp \longmapsto \CodonTransitionMatrixUp \longmapsto \SpectralStabilizationUp \longmapsto \DoobSurvivalChainUp \longmapsto \HostPrimitiveLeakageUp .
$$
The read exposes the active-triple ledger, median-output ledger, inactive-output row, centrality ledger, and direct-output multiplicities before it reaches any spectral stabilization, survival-chain, or host-primitive refusal consumer. In particular, a leakage multiplicity may not be read from $D$ without the rows $A,M,I,G$ that certify the finite table from which it came.
\end{theorem}
\begin{proof}
Let $L=(W,T,A,M,I,G,D,H,C,P,N)$ be accepted. Carrier projection first exposes the codon source window and finite transition vocabulary, so the six-bit median readback is tied to the same finite codon surface throughout the packet.

Replay $C$. The leakage request passes through the active triples, median outputs, inactive outputs, centrality ledger, and direct multiplicity row in sequence. Thus $D$ cannot be consumed unless $A,M,I,G$ have already been displayed.

The remaining siblings consume the displayed route. $\SpectralStabilizationUp$ reads the finite spectrum boundary, $\DoobSurvivalChainUp$ reads the conditioned survival-chain corridor, and $\HostPrimitiveLeakageUp$ refuses any replacement by host primitive enumeration. Transport through $H$ and provenance through $P,N$ preserve the same dependency route.
\end{proof}

\falsifiablePrediction{Every accepted consumer that reads a $\MedianLeakageSpectrumUp$ leakage multiplicity without the active-triple row, median-output row, inactive-output row, and centrality ledger refutes the packet.}

\independenceWitness{codon-six-bit-window, codon-transition-matrix, spectral-stabilization, doob-survival-chain, hostprimitiveleakage: $\MedianLeakageSpectrumUp$ is not bijective to any listed sibling because it jointly carries active triples, median outputs, inactive leakage rows, centrality counts, direct-output multiplicities, transport, replay, provenance, and local naming.}

The Lean follow-up for \texttt{BEDC.Derived.MedianLeakageSpectrumUp} must supply explicit $\mathsf{Nontrivial}\ \MedianLeakageSpectrumUp$ and $\mathsf{FieldFaithful}\ \MedianLeakageSpectrumUp$ instances preserving $W,T,A,M,I,G,D,H,C,P,N$ as separate displayed fields.

\closureat{MedianLeakageSpectrumUp}{seedStr}

\begin{closurestatus}{\MedianLeakageSpectrumUp}
  \constructivestory{A $\MedianLeakageSpectrumUp$ packet is generated from a CodonSixBitWindow source row, CodonTransitionMatrix vocabulary row, active triples, median outputs, inactive leakage rows, centrality counts, direct-output multiplicities, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:median-leakage-spectrum-carrier}, \autoref{thm:median-leakage-spectrum-namecert-obligations}, and \autoref{thm:median-leakage-spectrum-direct-output-route} seed the finite median-leakage spectrum surface for codon-window, transition, spectral, survival-chain, and host-primitive refusal consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological translation identity, stochastic model selection, quotient codon equality, host primitive enumeration, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, active-triple exactness, median-output exactness, inactive-output exactness, centrality and multiplicity ledgers, transport, replay, provenance, local naming, Nontrivial MedianLeakageSpectrumUp, and FieldFaithful MedianLeakageSpectrumUp for BEDC.Derived.MedianLeakageSpectrumUp.}
\end{closurestatus}
