\chapter{A Concrete Naming Certificate for $\ConnectedSpaceUp$}
\label{ch:concrete-instances-connected-space-namecert}
\origin{human}

Following Hausdorff and Bishop--Bridges topology, the $\ConnectedSpaceUp$ packet records connectedness as a finite refusal surface for displayed clopen separations over $\TopologyUp$. It sits beside the topology carrier of \autoref{ch:concrete-instances-topology-namecert}, the metric and real consumers of \autoref{ch:concrete-instances-metric-namecert} and \autoref{ch:concrete-instances-real-namecert}, the continuity route of \autoref{ch:concrete-instances-continuous-namecert}, the circle boundary of \autoref{ch:concrete-instances-s1-namecert}, and the chain-connected metric comparison of $\ChainConnectedMetricUp$. The certificate names the topological connectedness interface without adding excluded-middle separation, host subset extensionality, open-cover compactness, or a selected global point.

\begin{definition}[ConnectedSpace carrier]
\label{def:connected-space-carrier}
A $\ConnectedSpaceUp$ carrier is a finite $\BHist$ packet
$$
K=(T,O,S,F,M,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\TopologyUp$ open-set classifier row, including the visible open indices, membership ledger, finite meet rows, union rows, and boundary opens inspected by connectedness consumers.
\item $O$ is the clopen candidate row. It records a displayed open row together with the complementary open row that would form a separation if both sides were inhabited in the accepted packet.
\item $S$ is the clopen-separation attempt row. It stores the finite attempt to split the carrier into two disjoint nonempty clopen pieces and marks the route as refused unless the attempt collapses to the empty or whole boundary row already present in $T$.
\item $F$ is the $\ContinuousUp$ pullback row. It records only displayed inverse-image opens and their transported clopen attempts for continuous consumers.
\item $M$ is the optional $\MetricUp$ consumer row, used when a metric-generated topology requests connectedness data through balls and finite open ledgers.
\item $R$ is the optional $\RealUp$ consumer row, used by real-line and interval routes after the topology and pullback rows have been displayed.
\item $Q$ is the $\ChainConnectedMetricUp$ comparison row. It records that a metric chain-connected witness may feed the topological refusal surface only through the visible metric, topology, and real rows.
\item $H$ records componentwise $\hsame$ transport for the topology classifier, clopen attempt, pullback, optional metric and real consumers, chain-connected comparison, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a connectedness read through
$$
T,O,S,F,M,R,Q \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\ConnectedSpaceUp$, $\TopologyUp$, $\ContinuousUp$, $\MetricUp$, $\RealUp$, the $S^1$ circle source, $\ChainConnectedMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ConnectedSpaceUp}$ row.
\end{enumerate}
The carrier has no coordinate for excluded-middle decomposition of subsets, host subset extensionality, quotient topology equality, open-cover compactness, global choice of a point, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[ConnectedSpace carrier admission]
\label{thm:connected-space-carrier-admission}
For every accepted $\ConnectedSpaceUp$ carrier
$$
K=(T,O,S,F,M,R,Q,H,C,P,N),
$$
the local carrier admission row is exhausted by the displayed topology classifier, clopen attempt, continuous pullback, optional metric and real consumers, chain-connected comparison, componentwise transport, replay, provenance, and local naming rows. No connectedness consumer may inspect a clopen separation before those rows are present.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:connected-space-carrier}. The projection exposes exactly the rows $T,O,S,F,M,R,Q,H,C,P,N$.

The topology row is read first, because every clopen attempt is expressed as a pair of displayed open rows over the same $\TopologyUp$ classifier. The optional metric, real, circle, and chain-connected consumers are downstream rows; they do not add a second connectedness carrier.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier definition contains no further coordinate, carrier admission is precisely the displayed finite packet.
\end{proof}

\begin{theorem}[ConnectedSpace classifier stability]
\label{thm:connected-space-classifier-stability}
Let $K=(T,O,S,F,M,R,Q,H,C,P,N)$ and $K'=(T',O',S',F',M',R',Q',H',C',P',N')$ be accepted $\ConnectedSpaceUp$ carriers. If the topology classifier rows are $\hsame$, the clopen-attempt rows are transported by the displayed component of $H$, and the consumer rows $F,M,R,Q$ match componentwise, then every connectedness read accepted for $K$ is accepted for $K'$ through the same replay and provenance route.
\end{theorem}
\begin{proof}
Use the componentwise transport row in $H$. It carries the topology classifier first, so the open indices, membership ledger, finite meets, unions, and boundary opens remain the same visible topology surface.

Transport the clopen-attempt row next. The attempt remains a displayed open-complement pair over the transported topology classifier, and its refusal status remains attached to the same empty-or-whole boundary alternatives.

The rows $F,M,R,Q$ are transported after the classifier and attempt rows. Thus continuous, metric, real, circle, and chain-connected consumers receive the same finite route, and $C,P,N$ replay, source, and name that route for $K'$.
\end{proof}

\begin{theorem}[ConnectedSpace clopen-separation refusal]
\label{thm:connected-space-clopen-separation-refusal}
For an accepted $\ConnectedSpaceUp$ carrier $K=(T,O,S,F,M,R,Q,H,C,P,N)$, every clopen separation attempt in $S$ is refused unless the displayed clopen row in $O$ collapses through $T$ to the empty boundary open or to the whole-carrier boundary open. The refusal is a finite ledger row and is not an appeal to excluded middle over arbitrary subsets.
\end{theorem}
\begin{proof}
Read the attempt row $S$ together with the clopen row $O$. Both rows are indexed by the open-set classifier $T$, so the only admissible alternatives are the displayed boundary opens already present in the topology packet.

If the candidate is the empty boundary, the attempted separation has no left inhabited component. If the candidate is the whole-carrier boundary, the complementary side has no displayed inhabited component.

All other attempts remain refused by the local row $S$. The refusal is stored as finite NameCert data over $T,O,H,C,P,N$, so it does not decide arbitrary host subsets or import a global separation principle.
\end{proof}

\begin{theorem}[ConnectedSpace continuous-pullback preservation]
\label{thm:connected-space-continuous-pullback-preservation}
Let $K=(T,O,S,F,M,R,Q,H,C,P,N)$ be an accepted $\ConnectedSpaceUp$ carrier. Any $\ContinuousUp$ consumer that pulls a clopen attempt back along a displayed map must read the inverse-image row through $F$ and then reuse the same refusal route $T,O,S,H,C,P,N$. Hence the pullback of a refused clopen separation remains refused inside the connectedness packet.
\end{theorem}
\begin{proof}
Project the pullback row $F$. It stores only displayed inverse images of open rows from the topology classifier and their transported clopen attempts.

Apply the refusal theorem to the transported attempt. The pullback candidate is still read as a clopen row over $T$ and can pass only if it collapses to the displayed empty or whole boundary row.

The replay and provenance rows do not create a new separation object. They only route the continuous consumer through $F$ and back to $T,O,S,H,P,N$, so the refused status is preserved.
\end{proof}

\begin{theorem}[ConnectedSpace ledger nonescape]
\label{thm:connected-space-ledger-nonescape}
Every $\ConnectedSpaceUp$ read exported from an accepted carrier
$$
K=(T,O,S,F,M,R,Q,H,C,P,N)
$$
factors through $\TopologyUp$, $\ContinuousUp$, optional $\MetricUp$ and $\RealUp$ consumers, the $S^1$ circle source, $\ChainConnectedMetricUp$ comparison, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$. It exports no excluded-middle clopen split, no host subset extensionality, no quotient topology equality, no open-cover compactness, and no selected global point.
\end{theorem}
\begin{proof}
Combine carrier admission with the classifier-stability and clopen-refusal theorems. These place every accepted read inside the finite rows $T,O,S,F,M,R,Q,H,C,P,N$.

The continuous-pullback theorem handles the only consumer route that can manufacture a new clopen attempt. The attempt is immediately returned to the same refusal ledger.

Since the optional metric, real, circle, and chain-connected rows are consumer handoffs rather than generators of a host separation principle, the listed route exhausts the export surface and none of the refused objects can escape the ledger.
\end{proof}

\closureat{ConnectedSpaceUp}{seedStr}

\begin{closurestatus}{\ConnectedSpaceUp}
  \constructivestory{A $\ConnectedSpaceUp$ packet is generated from a Topology open-set classifier, a displayed clopen-attempt row, a finite refusal ledger, continuous pullback rows, optional Metric and Real consumer rows, a circle-source handoff, a ChainConnectedMetric comparison row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:connected-space-carrier}, \autoref{thm:connected-space-carrier-admission}, \autoref{thm:connected-space-classifier-stability}, \autoref{thm:connected-space-clopen-separation-refusal}, \autoref{thm:connected-space-continuous-pullback-preservation}, and \autoref{thm:connected-space-ledger-nonescape} seed the finite connectedness refusal surface over topology, continuity, metric, real, circle, and chain-connected consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close excluded-middle separation, host subset extensionality, quotient topology equality, open-cover compactness, selected points, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, clopen-separation refusal, continuous-pullback preservation, and ledger nonescape for BEDC.Derived.ConnectedSpaceUp.}
\end{closurestatus}
