\chapter{A Concrete Naming Certificate for $\ProperMapUp$}
\label{ch:concrete-instances-proper-map-namecert}
\origin{human}

Following Bourbaki and Kelley on proper maps between locally controlled metric
spaces, the $\ProperMapUp$ packet records the constructive boundary where a
continuous map is certified by finite compact-preimage evidence. It consumes
the metric rows of \autoref{ch:concrete-instances-metric-namecert}, the graph
and modulus rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the
compact metric evidence of \autoref{ch:concrete-instances-compactmetric-namecert},
the completion-facing handoff of
\autoref{ch:concrete-instances-metriccompletion-namecert}, and the terminal
real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet
names the proper-map interface as finite BEDC evidence rather than as host
topological prose.

\begin{definition}[Proper map carrier]
\label{def:proper-map-carrier}
A $\ProperMapUp$ carrier is a finite $\BHist$ packet
$$
M=(X,Y,F,K,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the certified source metric row, read through the $\MetricUp$
carrier, classifier, distance ledger, and local naming surface;
\item $Y$ is the certified target metric row, read through the same metric
certificate discipline;
\item $F$ is the $\ContinuousMapUp$ graph and modulus row from $X$ to $Y$,
including the finite graph ledger and the modulus route exposed to consumers;
\item $K$ is the compact-preimage witness row, assigning each displayed compact
metric target window to a displayed compact source window before any downstream
consumer reads the preimage;
\item $E$ is the $\MetricCompletionUp$ handoff row, recording that completion
consumers may read the properness boundary only after the compact-preimage row
and the continuous-map row have been replayed;
\item $H$ is the componentwise $\hsame$ transport row for $X,Y,F,K,E$;
\item $C$ is the displayed $\Cont$ replay route for accepted proper-map reads;
\item $P$ is the $\Pkg$ provenance over $\ProperMapUp$, $\MetricUp$,
$\ContinuousMapUp$, $\CompactMetricUp$, $\MetricCompletionUp$, $\RealUp$,
$\BHist$, $\hsame$, $\Cont$, and the local naming row;
\item $N$ is the local $\NameCert_{\ProperMapUp}$ row.
\end{enumerate}
The carrier imports no open-cover compactness, no host function equality, no
quotient completion, no countable choice, and no ambient $\RealUp$
completeness.
\end{definition}

\begin{definition}[Proper map classifier]
\label{def:proper-map-classifier}
Two accepted $\ProperMapUp$ carriers
$$
M=(X,Y,F,K,E,H,C,P,N)
\quad\hbox{and}\quad
M'=(X',Y',F',K',E',H',C',P',N')
$$
are classified as the same local proper-map datum exactly when the source
metric rows, target metric rows, continuous-map graph and modulus rows,
compact-preimage witness rows, and completion handoff rows are componentwise
identified by the displayed $\hsame$ transports and replay through the same
properness route. The classifier compares only these finite rows. It does not
compare host functions, quotient completions, open-cover compactness proofs, or
ambient real-completeness witnesses.
\end{definition}

\begin{theorem}[Proper map NameCert obligations]
\label{thm:proper-map-namecert-obligations}
For every accepted $\ProperMapUp$ carrier $M=(X,Y,F,K,E,H,C,P,N)$, the local
$\NameCert_{\ProperMapUp}$ surface consists of five finite obligations:
\begin{enumerate}
\item carrier admission for the displayed source and target metric rows,
continuous-map graph and modulus row, compact-preimage witness row,
completion handoff row, transports, replay route, provenance, and local naming;
\item classifier transport for the same displayed source, target, map,
compact-preimage, and completion rows under $\hsame$;
\item compact-preimage stability, requiring every target compact-window read to
be routed through $K$ before a source compact-window witness is exposed;
\item completion handoff compatibility, requiring every completion-facing
consumer to replay $F$ and $K$ before reading the row $E$;
\item non-escape, excluding open-cover compactness, host function equality,
quotient completion, countable choice, and ambient $\RealUp$ completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:proper-map-carrier}. The rows
$X,Y,F,K,E,H,C,P,N$ are exactly the displayed packet coordinates available to
the local certificate.

Classifier transport is componentwise. The row $H$ transports the metric rows,
the continuous-map graph and modulus row, the compact-preimage witness row, and
the completion handoff row without adding any host map equality or quotient
completion comparison.

Compact-preimage stability is the obligation carried by $K$. A target compact
window can be used by a consumer only after $K$ has displayed the matching
source compact window, so the route is finite and certificate-local.

Completion handoff compatibility follows from the placement of $E$. The handoff
row is downstream of the continuous-map and compact-preimage rows; replay
through $C$ must therefore pass through $F$ and $K$ before a completion-facing
consumer can read $E$.

The refusal clause is an inventory check on the packet. None of the nine rows
stores open-cover compactness, host function equality, quotient completion,
countable choice, or ambient real completeness, so the local certificate exports
none of those principles.
\end{proof}

\begin{theorem}[Proper map compact-preimage boundary]
\label{thm:proper-map-compact-preimage-boundary}
Every public compact-preimage read of an accepted $\ProperMapUp$ packet factors
through the row $K$ between the target $\CompactMetricUp$ evidence and the
source $\CompactMetricUp$ evidence. The route may inspect the metric rows
$X,Y$ and the continuous-map row $F$, then it must replay $K,H,C,P,N$ before it
exports a compact source-window witness. No public read may replace this route
by open-cover compactness, a host inverse image, a selected finite subcover, or
ambient real completeness.
\end{theorem}
\begin{proof}
Begin with the target compact-window request. The request is meaningful only
relative to the target metric row $Y$ and the continuous-map row $F$.

Apply the compact-preimage row $K$. It is the only coordinate that connects a
target compact-window read to a source compact-window witness, and it is stored
inside the finite packet.

Replay the result through $H,C,P,N$. These rows transport the displayed metric,
map, and compact-preimage data, record the continuation route, and preserve the
local provenance and naming boundary.

Since the exported source witness is obtained entirely from these packet rows,
there is no access to open-cover compactness, a host inverse image, a selected
finite subcover, or ambient real completeness.
\end{proof}

\begin{theorem}[Proper map completion handoff]
\label{thm:proper-map-completion-handoff}
Every completion-facing consumer of an accepted $\ProperMapUp$ packet reaches
the $\MetricCompletionUp$ row $E$ only after reading the source and target
metric rows, the $\ContinuousMapUp$ graph and modulus row, and the
compact-preimage witness row. Thus properness is handed to completion arguments
as finite BEDC evidence rather than as quotient completion, host function
equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the packet order in \autoref{def:proper-map-carrier}. The completion
handoff row $E$ is placed after $X,Y,F,K$ and before the transport, replay,
provenance, and local name rows.

A completion-facing consumer therefore reaches $E$ only through the replay
route $C$ after the continuous-map row $F$ and the compact-preimage row $K$ have
been displayed. The transports $H$ keep the source, target, map, preimage, and
handoff rows aligned under $\hsame$.

The handoff is consequently a finite BEDC route. It carries no quotient
completion constructor, no host function equality row, no countable-choice
selector, and no ambient $\RealUp$ completeness principle.
\end{proof}

\falsifiablePrediction{An accepted $\ProperMapUp$ consumer that reads a
$\MetricCompletionUp$ handoff or compact source-window witness without first
reading the displayed $X,Y,F,K$ rows refutes the carrier surface.}

\independenceWitness{metric, continuousmap, compactmetric, metriccompletion,
real: none is bijective to $\ProperMapUp$ because this packet jointly carries
source and target metric rows, a continuous-map graph and modulus row, a
compact-preimage witness row, a completion handoff row, transport, replay,
provenance, and local naming.}

\closureat{ProperMapUp}{seedStr}

\begin{closurestatus}{\ProperMapUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:proper-map-carrier}, \autoref{def:proper-map-classifier}, \autoref{thm:proper-map-namecert-obligations}, \autoref{thm:proper-map-compact-preimage-boundary}, and \autoref{thm:proper-map-completion-handoff} seed the finite proper-map certificate over metric rows, continuous-map rows, compact-preimage evidence, completion handoff, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, host function equality, quotient completion, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, compact-preimage stability, completion handoff compatibility, and ledger non-escape for BEDC.Derived.ProperMapUp.}
  \constructivestory{A $\ProperMapUp$ packet is generated from source and target metric rows, a ContinuousMapUp graph and modulus row, a compact-preimage witness row, a MetricCompletionUp handoff row, componentwise hsame transport, Cont replay, provenance, and local naming.}
\end{closurestatus}
