\chapter{A Concrete Naming Certificate for $\ValidatedNumericsUp$}
\label{ch:concrete-instances-validatednumerics-namecert}
\origin{human}

The $\ValidatedNumericsUp$ interface names certified finite real enclosures in
the interval-analysis tradition of Moore, but only through BEDC-visible
finite data. A packet carries displayed rational or dyadic endpoints, a
requested precision row, a regular rational observation window, a real-name
readback token, and a containment ledger whose reads are routed by $\Cont$.
It is therefore a consumer of $\DyadicRatCoreUp$, $\RationalIntervalUp$,
$\RegSeqRatUp$, $\RealUp$, and $\ModulusOfConvergenceUp$, not a theorem about
host floating-point arithmetic or external numerical solvers.

The precision-to-tail portion of the validated enclosure is consumed through
\autoref{ch:concrete-instances-dyadictailbound-namecert}. The
$\DyadicTailBoundUp$ packet supplies the dyadic tolerance,
$\CauchyModulusUp$ schedule, finite tail ledger, $\RegSeqRatUp$ readback, and
$\RealUp$ seal row that $\ValidatedNumericsUp$ reuses as its containment
ledger.

\begin{definition}[ValidatedNumerics BHist source]
\label{def:validatednumerics-bhist-source}
A $\ValidatedNumericsUp$ packet is a finite $\mathsf{BHist}$ tuple
$$
V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)
$$
with the following visible rows:
\begin{enumerate}
\item $I$ is a $\RationalIntervalUp$ enclosure row whose endpoints are read
  through $\RatUp$ or $\DyadicRatCoreUp$;
\item $\varepsilon$ is the requested precision row;
\item $\omega$ is a $\ModulusOfConvergenceUp$ row supplying the finite
  precision-to-window request used by the packet;
\item $\rho$ is a $\RegSeqRatUp$ observation window containing the displayed
  rational approximants inspected at that request;
\item $\lambda$ is a $\RealUp$ readback token for the real name being
  observed through the finite window;
\item $h$ records the componentwise $\hsame$ transports for the enclosure,
  precision, modulus, observation, readback, and containment rows;
\item $c$ records the $\Cont$ routes by which each displayed approximation is
  read inside the enclosure row $I$;
\item $p$ is the package provenance naming $\DyadicRatCoreUp$,
  $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, and
  $\ModulusOfConvergenceUp$;
\item $n$ is the local $\NameCert_{\ValidatedNumericsUp}$ registration row.
\end{enumerate}
The carrier predicate is
$\mathsf{ValidatedNumericsPacket}(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)$.
Its classifier compares two accepted packets only by transporting these
displayed rows and replaying the finite containment routes.
\end{definition}
\leandef{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsUp}
\leandef{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket}

\begin{theorem}[ValidatedNumerics interval enclosure obligation]
\label{thm:validatednumerics-interval-enclosure-obligation}
Every accepted $\ValidatedNumericsUp$ packet exposes one finite
$\RationalIntervalUp$ enclosure row $I$ and a containment ledger saying that
each displayed approximation read from the $\RegSeqRatUp$ window $\rho$
remains inside $I$ along a named $\Cont$ route. The obligation surface is the
enclosure row, endpoint provenance through $\DyadicRatCoreUp$ or $\RatUp$,
the precision request, the modulus row, the observation window, and the
containment ledger routed by $c$ and transported by $h$.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_interval\_enclosure\_obligation}
\begin{proof}
Project the carrier of
\autoref{def:validatednumerics-bhist-source}. The only interval coordinate is
$I$, and the only routes from displayed approximations to interval
containment are the $\Cont$ rows stored in $c$.

The endpoint source is read from the package provenance $p$, while
$\varepsilon$, $\omega$, and $\rho$ give the precision request, modulus row,
and regular rational observation window. Transporting the packet uses $h$ on
exactly those rows, so the accepted enclosure obligation is exhausted by the
finite packet coordinates.
\end{proof}

\begin{theorem}[ValidatedNumerics real readback soundness]
\label{thm:validatednumerics-real-readback-soundness}
For an accepted $\ValidatedNumericsUp$ packet
$V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)$, the $\RealUp$ readback token
$\lambda$ is sound only through the displayed $\RegSeqRatUp$ window $\rho$ and
the precision row supplied by $\ModulusOfConvergenceUp$. A consumer may read
the real name as a finite validated enclosure at the requested precision, but
the packet exports no general convergence proof, no classical real
completeness, and no equality of completed real representatives.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsReadbackPacket\_real\_readback\_soundness}
\begin{proof}
Read $\lambda$ together with $\rho$ and $\omega$ from the same carrier. The
token is not interpreted in isolation: the only available precision request
is $\varepsilon$, and the only finite observations attached to that request
are the displayed rows of $\rho$.

The containment routes from
\autoref{thm:validatednumerics-interval-enclosure-obligation} then place each
displayed approximation inside $I$. Repacking $\lambda$ with these window and
containment rows gives the finite readback soundness statement, while no
carrier coordinate remains for completeness or completed-real equality.
\end{proof}

\begin{theorem}[ValidatedNumerics finite-window Real seal containment]
\label{thm:validatednumerics-finite-window-real-seal-containment}
Let $V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)$ be an accepted
$\ValidatedNumericsUp$ packet. Any finite-window $\RealUp$ seal read whose
source is routed through the displayed $\RegSeqRatUp$ window $\rho$, the
$\ModulusOfConvergenceUp$ row $\omega$, and the packet $\Cont$ containment
ledger lands in the same $\RationalIntervalUp$ enclosure row $I$.

The conclusion is a finite enclosure statement over the packet surface. It
does not assert solver correctness, floating-point semantics, classical real
completeness, or equality of completed representatives.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_finite\_window\_seal\_containment}
\begin{proof}
Project the accepted packet. By
\autoref{thm:validatednumerics-interval-enclosure-obligation}, the only
enclosure exported by the carrier is $I$, and the only routes from displayed
$\RegSeqRatUp$ observations into an interval are the $\Cont$ ledger rows
stored in $c$.

Next read the $\RealUp$ token through
\autoref{thm:validatednumerics-real-readback-soundness}. The readback is
available only with the finite window $\rho$ and the modulus row $\omega$,
so the seal has no independent completed-real interface through which it
could choose a second enclosure.

The $\StreamNameUp$ finite-window handoff and the $\RegSeqRat$ finite-window
$\RealUp$ seal interface therefore expose the same consumer rows: the window
$\rho$, the modulus row $\omega$, the transported $\hsame$ rows, and the
$\Cont$ ledger. Repacking those rows gives containment in $I$, and the
packet contains no additional consumer row for solver semantics, hardware
floating-point interpretation, completeness, or equality of completions.
\end{proof}

\begin{theorem}[ValidatedNumerics precision refinement containment]
\label{thm:validatednumerics-precision-refinement-containment}
Let $V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)$ be an accepted
$\ValidatedNumericsUp$ packet. Suppose $V'$ refines the requested precision row
to a smaller finite request while preserving the same $\RationalIntervalUp$
enclosure $I$, the $\ModulusOfConvergenceUp$ row, the $\RegSeqRatUp$
observation window, the $\RealUp$ readback token, the displayed $\hsame$
transports, and the $\Cont$ containment routes. Then every approximation read
from the refined request is still contained in the same finite enclosure row
$I$.

The refinement is entirely internal to the displayed packet surface. It
introduces no solver-correctness theorem, no floating-point hardware
semantics, and no $\RealUp$ completeness datum beyond the readback token
already carried by $V$.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsReadbackPacket\_precision\_refinement\_containment}
\begin{proof}
Project the packet source using
\autoref{def:validatednumerics-bhist-source}. The refined request changes only
the finite precision row; the enclosure $I$, modulus row, observation window,
readback token, transport rows, containment routes, package provenance, and
local name row remain the displayed coordinates of the packet.

Apply \autoref{thm:validatednumerics-interval-enclosure-obligation}. Since the
same $\Cont$ containment routes are preserved, each refined approximation read
is routed back into the same finite enclosure row $I$.

Next apply \autoref{thm:validatednumerics-real-readback-soundness}. The
$\RealUp$ token stays tied to the displayed $\RegSeqRatUp$ window and the
finite modulus request, so refinement does not create a completed real object
or an external convergence principle.

Finally use \autoref{thm:validatednumerics-dependency-boundary}. Solver
correctness, floating-point semantics, and classical completeness are not
packet rows, hence they cannot enter the containment proof for the refined
read.
\end{proof}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_precision\_refinement\_containment}

\begin{theorem}[ValidatedNumerics five-row NameCert sketch]
\label{thm:validatednumerics-five-row-namecert-sketch}
The seed $\NameCert_{\ValidatedNumericsUp}$ surface is assembled from five
visible dependency rows:
\begin{enumerate}
\item a $\DyadicRatCoreUp$ endpoint or precision budget row;
\item a $\RationalIntervalUp$ enclosure row;
\item a $\ModulusOfConvergenceUp$ precision-to-window row;
\item a $\RegSeqRatUp$ observation-window row;
\item a $\RealUp$ readback row.
\end{enumerate}
Together with the containment ledger, $\hsame$ transports, $\Cont$ routes,
$\Pkg$ provenance, and local name row, these rows form the finite validated
numerics naming certificate.
\end{theorem}
\begin{proof}
Start from the packet coordinates in
\autoref{def:validatednumerics-bhist-source}. The five listed rows are exactly
the dependency-bearing coordinates: endpoints or precision budget from $I$
and $p$, the interval row $I$, the modulus row $\omega$, the observation row
$\rho$, and the readback token $\lambda$.

The remaining coordinates are structural. The transport row $h$ preserves the
displayed rows under classifier movement, $c$ routes containment reads, $p$
records the package provenance, and $n$ registers the local name. Repacking
these coordinates gives the seed naming-certificate surface without adding a
host numerical-analysis theorem.
\end{proof}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_five\_row\_namecert\_sketch}

\begin{theorem}[ValidatedNumerics dependency boundary]
\label{thm:validatednumerics-dependency-boundary}
The dependency boundary of $\ValidatedNumericsUp$ is precisely
$\DyadicRatCoreUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, and
$\ModulusOfConvergenceUp$, together with the BEDC kernel rows
$\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The packet does not
depend on floating-point hardware semantics, a solver-correctness theorem, a
classical completeness principle for real numbers, or a global convergence
claim beyond the displayed finite modulus request.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsKernel\_dependency\_boundary}
\begin{proof}
Inspect the package row $p$ of
\autoref{def:validatednumerics-bhist-source}. It names exactly the five
concrete dependency surfaces listed in the statement, and every consumer read
passes through the kernel rows $h$, $c$, $p$, and $n$.

The interval enclosure obligation and real readback soundness theorems use no
other coordinate. Since floating-point execution, solver correctness,
classical completeness, and global convergence are not rows of the finite
packet, they are outside the dependency boundary.
\end{proof}

\begin{theorem}[ValidatedNumerics carrier and classifier obligations]
\label{thm:validatednumerics-carrier-classifier-obligations}
The nine displayed rows of
\autoref{def:validatednumerics-bhist-source} supply the local carrier and
classifier obligations for $\ValidatedNumericsUp$. The carrier is inhabited by
any finite packet whose interval, precision, modulus, observation, readback,
transport, containment, package, and local name rows are displayed. Its
classifier compares accepted packets componentwise through the interval row,
precision row, modulus request, regular rational window, real readback token,
containment routes, $\hsame$ transport, $\mathsf{Pkg}$ provenance, and local
$\NameCert$ row, and carrier transport is exactly transport of these nine rows.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_carrier\_classifier\_obligations}
\begin{proof}
Read the packet definition row by row. Inhabitation is the assertion that the
displayed finite tuple
$V=(I,\varepsilon,\omega,\rho,\lambda,h,c,p,n)$ is present as a
$\mathsf{BHist}$ packet, so no additional analytic carrier is required.

For classifier laws, compare two accepted packets only through the nine
coordinates listed in the definition. The interval, precision, modulus,
observation, and readback entries are component rows, while $h$, $c$, $p$, and
$n$ record the transport, continuation, package, and local naming data used by
the comparison.

Carrier transport is therefore componentwise. Moving an accepted packet along
the displayed $\hsame$ rows and replaying the same $\Cont$ containment routes
keeps the tuple inside the carrier, with the package and local name rows
recording the same source surface.
\end{proof}

\begin{theorem}[ValidatedNumerics containment ledger transport]
\label{thm:validatednumerics-containment-ledger-transport}
Interval containment ledgers in an accepted $\ValidatedNumericsUp$ packet are
preserved by the displayed $\hsame$ and $\Cont$ rows. If the enclosure row,
precision request, modulus row, regular rational observation window, and
$\RealUp$ readback token are transported componentwise, then every containment
read from the transported observation window lands in the transported
$\RationalIntervalUp$ enclosure through the transported $\Cont$ ledger.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_containment\_ledger\_transport}
\begin{proof}
Start with \autoref{thm:validatednumerics-interval-enclosure-obligation}. It
identifies the containment ledger as the finite list of $\Cont$ routes from
displayed approximations in $\rho$ into the interval row $I$.

Transport the packet componentwise using the $h$ rows of
\autoref{def:validatednumerics-bhist-source}. The source approximation row, the
target interval row, the precision request, the modulus row, and the real
readback token move together, so the containment source and target remain
matched.

Finally replay the transported $c$ rows. Each ledger entry is a displayed
continuation route, hence it remains a continuation route after transport and
preserves the same finite containment claim inside the transported enclosure.
\end{proof}

\begin{theorem}[ValidatedNumerics refined readback containment determinacy]
\label{thm:validatednumerics-refined-readback-containment-determinacy}
Let $V$ and $V'$ be accepted $\ValidatedNumericsUp$ packets with the same
transported interval row, precision request, modulus request, $\RegSeqRatUp$
observation window, $\RealUp$ readback token, containment ledger, $\hsame$
transports, $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row. After
any displayed precision refinement of the request, the two packets yield the
same public finite-enclosure read.

The determinacy is only a finite readback boundary. It does not assert solver
correctness, hardware semantics, completed-real equality, or classical
completeness.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_refined\_readback\_containment\_determinacy}
\begin{proof}
First apply \autoref{thm:validatednumerics-real-readback-soundness}. The
common $\RealUp$ token is read through the same $\RegSeqRatUp$ observation
window and finite modulus request, so both packets expose the same real-name
readback row.

Next use \autoref{thm:validatednumerics-precision-refinement-containment}. A
displayed precision refinement narrows the requested finite enclosure by the
same transported interval row and the same modulus request on both sides.

Finally apply \autoref{thm:validatednumerics-containment-ledger-transport}.
The containment ledger, $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance,
and local $\NameCert$ row are shared, so the refined containment read is
transported identically for $V$ and $V'$. Therefore the public finite-enclosure
read after refinement is the same, while solver correctness, hardware
semantics, completed-real equality, and classical completeness remain outside
the packet.
\end{proof}

\begin{theorem}[ValidatedNumerics NameCert obligation surface]
\label{thm:validatednumerics-namecert-obligation-surface}
The $\NameCert_{\ValidatedNumericsUp}$ obligation surface is assembled from the
carrier and classifier obligations of
\autoref{thm:validatednumerics-carrier-classifier-obligations}, the interval
enclosure obligation of
\autoref{thm:validatednumerics-interval-enclosure-obligation}, the real readback
soundness of \autoref{thm:validatednumerics-real-readback-soundness}, precision
refinement containment from
\autoref{thm:validatednumerics-precision-refinement-containment}, containment
ledger transport from
\autoref{thm:validatednumerics-containment-ledger-transport}, package
provenance, and the local $\NameCert$ row.

This obligation surface is finite over $\DyadicRatCoreUp$,
$\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$,
$\ModulusOfConvergenceUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\mathsf{Pkg}$, and $\NameCert$, and it does not assert solver correctness,
floating-point hardware semantics, host real equality, or classical real
completeness.
\end{theorem}
\begin{proof}
First assemble the carrier and classifier rows from
\autoref{thm:validatednumerics-carrier-classifier-obligations}. These rows bind
the accepted packet to the nine displayed coordinates of the source definition.

Next attach the enclosure and readback rows. Apply
\autoref{thm:validatednumerics-interval-enclosure-obligation} for the interval
ledger and \autoref{thm:validatednumerics-real-readback-soundness} for the
$\RealUp$ token read through the $\RegSeqRatUp$ window and finite modulus
request.

The refinement and transport rows are supplied by
\autoref{thm:validatednumerics-precision-refinement-containment} and
\autoref{thm:validatednumerics-containment-ledger-transport}. They keep the
finite enclosure claim stable under smaller precision requests and displayed
$\hsame/\Cont$ movement.

Finally add the package provenance and local naming row from
\autoref{def:validatednumerics-bhist-source}. Together with
\autoref{thm:validatednumerics-dependency-boundary}, this exhausts the local
obligation surface and leaves solver correctness, floating-point semantics,
host real equality, and classical completeness outside the packet.
\end{proof}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_namecert\_obligation\_surface}

\begin{theorem}[ValidatedNumerics obligation closure scope]
\label{thm:validatednumerics-obligation-closure-scope}
The finite enclosure packet obligations for $\ValidatedNumericsUp$ are
exhausted by the displayed $\DyadicRatCoreUp$ or $\RatUp$ endpoint row, the
$\RationalIntervalUp$ enclosure row, the $\ModulusOfConvergenceUp$
precision-to-window row, the $\RegSeqRatUp$ observation window, the $\RealUp$
readback row, the containment ledger, $\hsame$ transports, $\Cont$ routes,
$\mathsf{Pkg}$ provenance, and the local $\NameCert$ rows.

No obligation row in this scope asserts host numerical-solver correctness,
floating-point hardware semantics, completed-real equality, or a global
convergence theorem beyond the displayed finite modulus request.
\end{theorem}
\begin{proof}
Project the packet source of
\autoref{def:validatednumerics-bhist-source}. Its displayed coordinates are
the rational or dyadic endpoint data, the enclosure interval, the precision
request, the modulus-to-window row, the finite observation window, the
readback token, containment routes, transport row, package provenance, and
local name row.

Apply \autoref{thm:validatednumerics-interval-enclosure-obligation}. This
identifies the containment part of the obligation surface as the finite
enclosure row together with the displayed continuation ledger.

Next apply \autoref{thm:validatednumerics-real-readback-soundness}. The
readback obligation is tied to the $\RegSeqRatUp$ observation window and the
finite modulus request, so it contributes no completed-real equality or
external convergence principle.

Finally use \autoref{thm:validatednumerics-five-row-namecert-sketch} and
\autoref{thm:validatednumerics-dependency-boundary}. The five dependency rows
and the BEDC kernel rows listed there exhaust the local naming surface, while
solver correctness, floating-point hardware semantics, classical completeness,
and global convergence remain outside the packet boundary.
\end{proof}

\begin{theorem}[ValidatedNumerics exported enclosure bridge]
\label{thm:validatednumerics-exported-enclosure-bridge}
The public $\ValidatedNumericsUp$ export bridges a finite validated enclosure
packet to exactly the displayed boundary consisting of the
$\RationalIntervalUp$ enclosure, the dyadic or rational endpoint row, the
finite modulus request, the $\RegSeqRatUp$ observation window, the $\RealUp$
readback token, the containment ledger, $\hsame$ transports, $\Cont$ routes,
$\Pkg$ provenance, and the local $\NameCert$ row.

The bridge does not export solver correctness, floating-point hardware
semantics, host real equality, or classical completeness.
\end{theorem}
\begin{proof}
Start from the finite enclosure obligation. Apply
\autoref{thm:validatednumerics-interval-enclosure-obligation}; this fixes the
$\RationalIntervalUp$ enclosure, endpoint row, finite modulus request, and
continuation ledger as the carrier side of the public packet.

Next attach the real readback boundary. Apply
\autoref{thm:validatednumerics-real-readback-soundness}; the $\RealUp$ token is
read only through the $\RegSeqRatUp$ observation window and finite modulus
request, so no host real equality is introduced.

The exported packet must remain stable under sharper finite requests. Apply
\autoref{thm:validatednumerics-precision-refinement-containment} and
\autoref{thm:validatednumerics-containment-ledger-transport}; refinement
narrows the interval while the hidden containment ledger is carried by the
displayed $\hsame$ transports and $\Cont$ routes.

Finally apply \autoref{thm:validatednumerics-namecert-obligation-surface}. The
local $\NameCert$ row and $\Pkg$ provenance repack the preceding rows as the
public bridge boundary. Since each step projects from the displayed finite
packet, solver correctness, floating-point hardware semantics, host real
equality, and classical completeness remain outside the bridge.
\end{proof}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsFiniteEnclosure\_exported\_bridge}

\begin{theorem}[ValidatedNumerics public finite-enclosure consumer certificate]
\label{thm:validatednumerics-public-finite-enclosure-consumer-certificate}
A scoped $\ValidatedNumericsUp$ packet exports a public finite-enclosure
consumer certificate. The interval enclosure obligation gives the carrier row,
real readback soundness gives the $\RealUp$ interpretation, precision refinement
containment supplies monotone narrowing, and containment ledger transport
records the hidden refinement ledger. Downstream $\RealUp$ and $\RegSeqRatUp$
consumers may use the enclosure packet without assuming any host real-number
primitive.
\end{theorem}
\begin{proof}
First build the finite enclosure source. Apply
\autoref{thm:validatednumerics-interval-enclosure-obligation}; the displayed
endpoint and interval rows provide the carrier-side enclosure data, while the
continuation routes record the finite containment obligation.

Next interpret the enclosure as a real readback packet. By
\autoref{thm:validatednumerics-real-readback-soundness}, the readback is routed
through the $\RegSeqRatUp$ observation window, the finite modulus request, and
the named $\RealUp$ row, so the consumer sees a BEDC real-name interpretation
rather than a host completed-real primitive.

The public certificate must also be stable under tighter requests. Apply
\autoref{thm:validatednumerics-precision-refinement-containment}; smaller
precision demands retain the enclosing row by monotone narrowing and preserve
the same displayed transport surface.

Finally apply
\autoref{thm:validatednumerics-containment-ledger-transport}. The hidden
refinement ledger is carried as $\Cont/\hsame$ provenance, not as a solver
oracle. Repacking these four rows gives a public finite-enclosure consumer
certificate usable by downstream $\RealUp$ and $\RegSeqRatUp$ consumers, with
solver correctness, floating-point semantics, and classical real completeness
remaining outside the exported packet.
\end{proof}

\begin{theorem}[ValidatedNumerics validated enclosure bridge boundary]
\label{thm:validatednumerics-validated-enclosure-bridge-boundary}
The public finite-enclosure consumer certificate of
\autoref{thm:validatednumerics-public-finite-enclosure-consumer-certificate}
and the $\NameCert$ obligation surface of
\autoref{thm:validatednumerics-namecert-obligation-surface} assemble a paper
bridge boundary whose readable rows are exactly the $\RationalIntervalUp$
enclosure, the $\DyadicRatCoreUp$ or $\RatUp$ endpoint provenance, the finite
$\ModulusOfConvergenceUp$ request, the $\RegSeqRatUp$ observation window, the
$\RealUp$ readback token, the containment ledger, the $\hsame$ transports, the
$\Cont$ routes, the $\Pkg$ provenance, and the local $\NameCert$ row.

Solver correctness, floating-point hardware semantics, host real equality, and
classical real completeness are not bridge rows.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsUp\_StdBridge}
\begin{proof}
Begin with the interval enclosure of
\autoref{thm:validatednumerics-interval-enclosure-obligation}. It supplies the
$\RationalIntervalUp$ enclosure together with dyadic or rational endpoint
provenance and the finite precision request visible to the consumer.

Next apply \autoref{thm:validatednumerics-real-readback-soundness}. The
readback token is interpreted through the $\RegSeqRatUp$ observation window and
the finite $\ModulusOfConvergenceUp$ request, so the row remains a displayed
BEDC real-name read rather than host real equality.

Use \autoref{thm:validatednumerics-precision-refinement-containment} and
\autoref{thm:validatednumerics-containment-ledger-transport} for the boundary
rows that survive sharper requests. They identify the containment ledger and
transport it through the displayed $\hsame$ and $\Cont$ surface.

Finally apply
\autoref{thm:validatednumerics-namecert-obligation-surface} and
\autoref{thm:validatednumerics-public-finite-enclosure-consumer-certificate}.
The $\NameCert$ surface supplies the local name and $\Pkg$ provenance, and the
consumer certificate repacks exactly those rows as the conservative bridge
boundary. Since every bridge row is projected from this finite packet, solver
correctness, floating-point hardware semantics, host real equality, and
classical real completeness remain outside the bridge boundary.
\end{proof}

\begin{theorem}[ValidatedNumerics finite consumer example completeness]
\label{thm:validatednumerics-finite-consumer-example-completeness}
Every finite consumer example using the displayed validated-enclosure bridge
of \autoref{thm:validatednumerics-validated-enclosure-bridge-boundary}
factors through the $\RationalIntervalUp$ enclosure row, dyadic-or-rational
endpoint provenance, finite $\ModulusOfConvergenceUp$ request,
$\RegSeqRatUp$ observation window, $\RealUp$ readback token, containment
ledger, visible $\hsame$ transports, visible $\Cont$ routes, $\mathsf{Pkg}$
provenance, and local $\NameCert_{\ValidatedNumericsUp}$ row.

Conversely, those displayed rows repack as a valid finite consumer example for
the validated-enclosure bridge. The repacking preserves the exclusions on
solver correctness, floating-point semantics, host real equality, and
classical real completeness.
\end{theorem}
\begin{proof}
Begin with a finite consumer example and apply
\autoref{thm:validatednumerics-public-finite-enclosure-consumer-certificate}.
The certificate projects the example to the rational-interval enclosure,
endpoint provenance, finite precision request, regular rational observation
window, real readback token, containment ledger, transport rows, package
provenance, and local naming row.

Next apply
\autoref{thm:validatednumerics-validated-enclosure-bridge-boundary}. It
identifies the same rows as the bridge boundary visible to downstream
consumers, so no solver, hardware, host-real, or classical-completeness
coordinate is introduced by the bridge read.

Use \autoref{thm:validatednumerics-precision-refinement-containment} to keep
the enclosure stable under finite precision requests. Then apply
\autoref{thm:validatednumerics-containment-ledger-transport} to carry the
containment ledger through the displayed $\hsame$ and $\Cont$ surface.

For the converse direction, start from the listed displayed rows. Repack the
enclosure row, endpoint provenance, finite modulus request, observation
window, readback token, containment ledger, transport rows, package provenance,
and local name row by the public finite-enclosure consumer certificate. The
validated-enclosure bridge boundary then reads exactly that packet as a valid
finite consumer example, with the same excluded semantic obligations remaining
outside the exported surface.
\end{proof}

\closureat{ValidatedNumericsUp}{seedStr}
\closureat{ValidatedNumericsUp}{obligationStr}
\closureat{ValidatedNumericsUp}{scopedStr}
\closureat{ValidatedNumericsUp}{publicStr}
\closureat{ValidatedNumericsUp}{bridgedStr}
\closureat{ValidatedNumericsUp}{matureStr}

\begin{closurestatus}{\ValidatedNumericsUp}
  \constructivestory{A $\ValidatedNumericsUp$ packet is generated by a rational or dyadic interval enclosure, a requested precision row, a finite modulus-of-convergence request, a regular rational observation window, a real-name readback token, containment routes, transport rows, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:validatednumerics-validated-enclosure-bridge-boundary} and \autoref{thm:validatednumerics-public-finite-enclosure-consumer-certificate} bind the finite certified-enclosure bridge surface over $\DyadicRatCoreUp$, $\RatUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\ModulusOfConvergenceUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\bridgeCheckedV}
  \leantarget{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsReadbackPacket\_real\_readback\_soundness}
  \bridgestatus{bridgeChecked}
  \origin{human}
  \notclaimed{This chapter does not close general convergence, floating-point hardware semantics, classical real completeness, or solver correctness.}
  \upgradepath{No further upgrade remains; the chapter is at the top of the formal axis.}
\end{closurestatus}

\begin{theorem}[ValidatedNumerics refinement composition containment]
\label{thm:validatednumerics-refinement-composition-containment}
Let
$$
\begin{aligned}
V_0&=(I,\varepsilon_0,\omega,\rho,\lambda,h,c,p_0,n_0),\\
V_1&=(I,\varepsilon_1,\omega,\rho,\lambda,h,c,p_1,n_1),\\
V_2&=(I,\varepsilon_2,\omega,\rho,\lambda,h,c,p_2,n_2)
\end{aligned}
$$
be accepted $\ValidatedNumericsUp$ packets. Suppose $V_1$ refines the
requested precision row of $V_0$ to a smaller finite request, and $V_2$
refines the requested precision row of $V_1$ to a smaller finite request.
Assume that both refinement steps preserve the displayed
$\RationalIntervalUp$ enclosure $I$, the $\ModulusOfConvergenceUp$ row
$\omega$, the $\RegSeqRatUp$ observation window $\rho$, the $\RealUp$
readback token $\lambda$, the $\hsame$ transport row $h$, and the $\Cont$
containment ledger $c$. Then the composite refinement from $V_0$ to $V_2$
routes every displayed approximation read at the terminal request into the
original finite enclosure row $I$ through the original containment ledger
$c$.

The conclusion is a containment statement over the displayed finite packet
surface. It does not add solver correctness, floating-point hardware
semantics, completed-real equality, or a global convergence principle.
\end{theorem}
\leanchecked{BEDC.Derived.ValidatedNumericsUp.ValidatedNumericsPacket\_refinement\_composition\_containment}
\begin{proof}
Project the three accepted packets through
\autoref{def:validatednumerics-bhist-source}. The first refinement changes
only the precision coordinate from $\varepsilon_0$ to $\varepsilon_1$ and
keeps $I$, $\omega$, $\rho$, $\lambda$, $h$, and $c$ fixed as displayed rows.
The second refinement changes only the precision coordinate from
$\varepsilon_1$ to $\varepsilon_2$ and keeps the same six displayed rows
fixed again.

By the classifier description in
\autoref{def:validatednumerics-bhist-source}, accepted packets are compared
componentwise by the displayed rows and by replay of the finite containment
routes. The two displayed comparisons therefore compose on the enclosure,
modulus, observation window, readback token, transport row, and containment
ledger. The transitivity part of
\autoref{thm:history-sameness-equivalence} supplies the corresponding
$\hsame$ comparison for the transported rows, so $V_2$ still displays the
same containment source window $\rho$, the same target enclosure $I$, and the
same ledger $c$ as $V_0$.

Apply \autoref{thm:validatednumerics-precision-refinement-containment} to the
second refinement $V_1$ to $V_2$. Since the enclosure row of $V_1$ is the
same displayed row $I$ inherited from $V_0$, every approximation read from
the terminal refined request is contained in $I$.

It remains only to identify this containment as a read through the original
ledger rather than through an unrelated copy. Apply
\autoref{thm:validatednumerics-containment-ledger-transport}. The source
approximation rows, the target interval row, the modulus row, the readback
token, and the containment routes are transported by the same $h$ and replay
the same $c$ at both refinement steps. Hence each terminal approximation read
from $V_2$ lands in the original finite enclosure row $I$ through the
original $\Cont$ routes recorded in $c$.

Finally, \autoref{thm:validatednumerics-real-readback-soundness} keeps the
readback token tied to the displayed $\RegSeqRatUp$ window and finite modulus
request, and \autoref{thm:validatednumerics-dependency-boundary} excludes any
extra analytic or host-numeric coordinate from the argument.
\end{proof}
