\chapter{A Concrete Naming Certificate for $\OnticAdequacyAuditUp$}
\label{ch:concrete-instances-ontic-adequacy-audit-namecert}
\origin{ai}

The $\OnticAdequacyAuditUp$ packet realizes the adequacy discipline of \autoref{ch:visions-reality-constrained-ontic-state} as one finite NameCert boundary. It sits after the ontic-source certificate of \autoref{ch:concrete-instances-onticstate-namecert}, the model-audit packet of \autoref{ch:concrete-instances-physical-model-audit-namecert}, the tower certificate of \autoref{ch:concrete-instances-reality-constrained-approximation-tower-namecert}, the stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real carrier of \autoref{ch:concrete-instances-real-namecert}. Its role is to bind source, audit, Real-facing readback, classifier, residue, transport, route, provenance, and local naming rows before signature exactness is read as ontic adequacy.

\begin{definition}[Ontic adequacy audit carrier]
\label{def:ontic-adequacy-audit-carrier}
An $\OnticAdequacyAuditUp$ carrier is a finite $\BHist$ packet
$$
A=(O,M,S,R,E,K,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the $\OnticStateUp$ source row naming the stable reality-facing source under audit.
\item $M$ is the $\PhysicalModelAuditUp$ row recording the finite source traces, observed signatures, model signatures, tower data, failure surface, strength, and audit ledger already accepted for the candidate model.
\item $S$ is the $\mathsf{StreamName}^{\uparrow}$ schedule row selecting the finite observation windows that may be used for adequacy readback.
\item $R$ is the $\mathsf{RegSeqRat}^{\uparrow}$ readback row attached to the scheduled windows.
\item $E$ is the $\RealUp$ facing row reached only through the displayed stream and regular-rational readback rows.
\item $K$ is the signature classifier row comparing the ontic source signatures with the audited model signatures at the declared adequacy level.
\item $L$ is the approximation and residue ledger, recording selected tower limits, rejected shortcut limits, unrepresented source content, and the gap between signature exactness and total ontic exhaustion.
\item $H$ records componentwise $\hsame$ transport for the source, audit, stream, regular-rational, Real-facing, classifier, ledger, route, provenance, and local naming rows.
\item $C$ records the displayed $\Cont$ route through $O,M,S,R,E,K,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\OnticAdequacyAuditUp$, $\OnticStateUp$, $\PhysicalModelAuditUp$, $\mathsf{StreamName}^{\uparrow}$, $\mathsf{RegSeqRat}^{\uparrow}$, $\RealUp$, $\RealityConstrainedApproximationTowerUp$, $\ObservationReflectionPacketUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\OnticAdequacyAuditUp}$ row.
\end{enumerate}
The carrier contains no coordinate for host truth, unbounded observation, selected limits outside $L$, quotient-real equality, Real completeness as physical adequacy, or a detached model-syntax route. Signature exactness may be read as ontic adequacy only through the full displayed packet.
\end{definition}
\leanchecked{BEDC.Derived.OnticAdequacyAuditUp.OnticAdequacyAuditTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Ontic adequacy audit NameCert obligations]
\label{thm:ontic-adequacy-audit-namecert-obligations}
For the carrier of \autoref{def:ontic-adequacy-audit-carrier}, the local $\NameCert_{\OnticAdequacyAuditUp}$ surface consists exactly of five obligation rows:
\begin{enumerate}
\item carrier admission for the finite packet $A=(O,M,S,R,E,K,L,H,C,P,N)$;
\item signature-exactness admission through the joint $\OnticStateUp$ source row $O$, $\PhysicalModelAuditUp$ audit row $M$, and classifier row $K$;
\item Real-facing readback admission through the displayed $\mathsf{StreamName}^{\uparrow}$, $\mathsf{RegSeqRat}^{\uparrow}$, and $\RealUp$ rows $S,R,E$;
\item residue-ledger exactness through $L$, including the selected tower limits, rejected shortcuts, and unrepresented source content;
\item non-escape from host truth, selected limits, quotient reals, Real completeness, and model syntax through componentwise transport, displayed replay, provenance, and local naming rows $H,C,P,N$.
\end{enumerate}
Thus an accepted adequacy read can promote signature exactness to ontic adequacy only when source trace, model audit, Real-facing readback, classifier, residue ledger, transport, route, provenance, and local name are displayed together.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:ontic-adequacy-audit-carrier}. The accepted tuple displays the ontic source $O$, the physical model audit $M$, the stream schedule $S$, the regular-rational readback $R$, the Real-facing row $E$, the classifier $K$, the residue ledger $L$, and the structural rows $H,C,P,N$.

The signature-exactness row is not a model-only comparison. It reads the source signatures from $O$, the audited model signatures from $M$, and the comparison row $K$ inside the same packet. The Real-facing readback is likewise constrained: $E$ is available only after the scheduled stream row $S$ and regular-rational row $R$ have been displayed.

The residue ledger closes the remaining adequacy boundary. Selected tower limits, rejected shortcut limits, and unrepresented source content must be recorded in $L$, so Real completion or quotient-real equality cannot replace the ledger. The rows $H,C,P,N$ only transport, replay, source, and name the displayed packet. They add no host truth oracle, no hidden physical-object coordinate, and no second route from model syntax to ontic adequacy.

Therefore the five listed rows exhaust the local NameCert surface, and every accepted adequacy read remains inside the finite packet $A$.
\end{proof}

The Lean TasteGate file \texttt{lean4/BEDC/Derived/OnticAdequacyAuditUp/TasteGate.lean} must provide explicit $\mathsf{Nontrivial}\ \OnticAdequacyAuditUp$ and $\mathsf{FieldFaithful}\ \OnticAdequacyAuditUp$ instances preserving $O,M,S,R,E,K,L,H,C,P,N$ as separate displayed fields.

\falsifiablePrediction{If the source-trace row or residue ledger is absent, no accepted OnticAdequacyAuditUp route can promote signature exactness to ontic adequacy.}

\independenceWitness{onticstate, physicalmodelaudit, realityconstrainedapproximationtower, observationreflectionpacket, real: none is bijective because the audit packet binds source, audit, Real-facing readback, classifier, residue, transport, route, provenance, and local naming rows together.}

\closureat{OnticAdequacyAuditUp}{seedStr}

\begin{closurestatus}{\OnticAdequacyAuditUp}
  \constructivestory{An $\OnticAdequacyAuditUp$ packet is generated from an ontic source row, physical model audit row, stream schedule, regular-rational readback, Real-facing row, signature classifier, approximation and residue ledger, componentwise hsame transport, displayed Cont route, Pkg provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:ontic-adequacy-audit-carrier} and \autoref{thm:ontic-adequacy-audit-namecert-obligations} bind the finite adequacy-audit carrier and its source, audit, readback, classifier, ledger, transport, route, provenance, and local naming obligations.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, total physical ontology, host truth, quotient-real adequacy, selected-limit sufficiency, Real completeness as physical adequacy, or model syntax as ontic adequacy.}
  \upgradepath{Obligation closure requires checked carrier admission, signature-exactness admission, Real-facing readback admission, residue-ledger exactness, non-escape, TasteGate nontriviality, and field faithfulness for $O,M,S,R,E,K,L,H,C,P,N$.}
\end{closurestatus}
