\chapter{A Concrete Naming Certificate for $\SturmComparisonUp$}
\label{ch:concrete-instances-sturm-comparison-namecert}
\origin{human}

Following Sturm comparison theory and Bishop--Bridges constructive analysis, the $\SturmComparisonUp$ packet records a finite comparison-neighbour surface for two displayed scalar ODE rows. It consumes the local-flow source of \autoref{ch:concrete-instances-ode-namecert}, the continuous-map handoff of \autoref{ch:concrete-instances-continuousmap-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the Sturm root-isolation sibling of \autoref{ch:concrete-instances-sturmrootisolation-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a local zero-order comparison certificate; it does not assert global ODE completeness, host solution equality, excluded-middle sign trichotomy, quotient real equality, or a selected classical solution curve.

\begin{definition}[Sturm comparison carrier]\label{def:sturm-comparison-carrier}
A $\SturmComparisonUp$ carrier is a finite $\BHist$ packet
$$
S=(O_0,O_1,K,Z,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O_0$ and $O_1$ are the two scalar $\OdeUp$ comparison-equation rows. Each row records its local time window, coefficient readbacks, initial endpoint data, and solution-window request through the displayed $\OdeUp$ local-flow surface.
\item $K$ is the coefficient-order ledger. It records the finite comparison inequalities between the two coefficient packets, including the time window on which the order is licensed and the continuous-map rows that transport coefficient observations.
\item $Z$ is the finite zero-window ledger. It records the inspected intervals, endpoint signs or nonzero certificates, retained zero-neighbour rows, and the local interlacing request used by the comparison read.
\item $W$ stores the $\StreamNameUp$ windows for coefficient observations, solution observations, and zero-window endpoints.
\item $R$ stores the $\RegSeqRatUp$ readbacks attached to the windows in $W$.
\item $E$ stores the $\RealUp$ seals for the coefficient-order rows, endpoint observations, and zero-window boundaries after $O_0,O_1,K,Z,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for both ODE rows, coefficient-order ledgers, zero-window rows, stream windows, regular readbacks, real seals, continuation replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a comparison request through the two ODE rows, coefficient order, zero windows, readbacks, seals, transport, provenance, and local name.
\item $P$ is the $\Pkg$ provenance over $\SturmComparisonUp$, $\OdeUp$, $\ContinuousMapUp$, $\SturmRootIsolationUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SturmComparisonUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite comparison packet. It has no coordinate for a host solution space, global existence theorem, solution equality, trichotomy oracle, quotient real stream, or ambient completeness principle.
\end{definition}

\begin{theorem}[Sturm comparison NameCert obligations]\label{thm:sturm-comparison-namecert-obligations}
For every accepted $\SturmComparisonUp$ carrier $S=(O_0,O_1,K,Z,W,R,E,H,C,P,N)$, the local $\NameCert_{\SturmComparisonUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the two displayed $\OdeUp$ comparison rows, coefficient-order ledger, finite zero-window ledger, stream windows, regular readbacks, real seals, transport, replay, provenance, and local naming;
\item coefficient-order exactness, requiring every comparison inequality to pass through $K$ and through the continuous-map rows named by the coefficient readbacks;
\item zero-window exactness, requiring every zero-neighbour and interlacing read to pass through $Z$ before any $\RealUp$ seal is exported;
\item readback confinement, requiring the windows $W$ and readbacks $R$ to mediate all coefficient, solution, and endpoint observations;
\item componentwise $\hsame$ transport and displayed $\Cont$ replay through $H$ and $C$;
\item provenance and local naming through $P$ and $N$.
\end{enumerate}
No comparison obligation outside these rows is part of the packet.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:sturm-comparison-carrier}. The two ODE rows $O_0,O_1$ supply the only local-flow source data, so a comparison read cannot inspect a solution before the displayed ODE windows and endpoint rows have been opened.

The coefficient-order surface is $K$. Its entries are finite Real-facing reads transported through continuous-map rows and the window/readback pair $W,R$, so the order relation is a certificate row rather than a host comparison of functions.

The zero-window surface is $Z$. It records the inspected windows, retained endpoint signs or nonzero witnesses, and the interlacing request. The $\RealUp$ seals in $E$ are downstream of $Z$, hence zero-order information cannot bypass the finite zero ledger.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since none of these structural rows adds a host solution space, quotient stream, trichotomy principle, or ambient completeness witness, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Sturm comparison zero-order handoff]\label{thm:sturm-comparison-zero-order-handoff}
Every downstream $\RealUp$, $\RegSeqRatUp$, or zero-window consumer of an accepted $\SturmComparisonUp$ packet reads the route
$$
O_0,O_1 \longmapsto K \longmapsto Z \longmapsto W,R \longmapsto E \longmapsto H,C,P,N
$$
before it may use the comparison conclusion. Thus the consumer receives two displayed $\OdeUp$ comparison rows, coefficient-order ledgers, finite zero-window rows, stream windows, regular readbacks, real seals, componentwise transport, displayed continuation replay, provenance, and local naming. It receives no global ODE completeness theorem, host solution equality, excluded-middle sign trichotomy, quotient real equality, or selected classical solution curve.
\end{theorem}
\begin{proof}
Begin with a consumer request for a comparison conclusion. The only source rows available are the two $\OdeUp$ rows $O_0,O_1$, so the request is already confined to displayed local-flow data.

Read the coefficient order through $K$. The order ledger is then tied to the finite observation rows $W,R$, which expose coefficient and endpoint values through $\StreamNameUp$ and $\RegSeqRatUp$ rather than through host real functions.

Read the zero-window ledger $Z$. The retained windows and interlacing request are the only zero-order data visible to the consumer, and the real seals $E$ are produced only after those windows have been displayed.

The rows $H,C,P,N$ repack the same route as transport, replay, provenance, and local naming. Therefore every accepted handoff is the finite comparison packet itself, with no separate classical comparison theorem or ambient completeness principle exported.
\end{proof}

\closureat{SturmComparisonUp}{seedStr}

\begin{closurestatus}{\SturmComparisonUp}
  \constructivestory{A $\SturmComparisonUp$ packet is generated from two displayed $\OdeUp$ comparison rows, coefficient-order ledgers, finite zero-window rows, $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\RealUp$ seals, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sturm-comparison-carrier}, \autoref{thm:sturm-comparison-namecert-obligations}, and \autoref{thm:sturm-comparison-zero-order-handoff} seed the finite comparison-neighbour packet over displayed ODE rows, coefficient order, zero windows, readbacks, and Real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global ODE completeness, host solution equality, excluded-middle sign trichotomy, quotient real equality, selected classical solution curves, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, coefficient-order exactness, zero-window exactness, readback confinement, consumer handoff, and structural stability for BEDC.Derived.SturmComparisonUp.}
\end{closurestatus}
