\chapter{A Concrete Naming Certificate for $\SequentialCompactUp$}
\label{ch:concrete-instances-sequentialcompact-namecert}
\origin{human}

Following Bishop and Bridges constructive compactness and Brouwer choice-sequence practice, the $\SequentialCompactUp$ packet records sequential compactness only as finite subsequence-window data. It sits over the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the Baire-space inspection discipline of \autoref{ch:concrete-instances-bairespace-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives compact-metric and Baire-space completion consumers a displayed subsequence route; it is not a host sequential compactness theorem, not countable choice, and not a quotient stream principle.

\begin{definition}[SequentialCompact carrier]
\label{def:sequential-compact-carrier}
A $\SequentialCompactUp$ carrier is a finite $\BHist$ packet
$$
Q=(K,B,S,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row whose finite cover and metric inspection data bound the sequence consumer.
\item $B$ is the $\BaireSpaceUp$ cylinder discipline row used when a downstream completion route reads finite choice-sequence windows.
\item $S$ is the $\StreamNameUp$ source-window row, recording the inspected indices and finite request schedule.
\item $W$ is the finite subsequence-window row: selected indices, selected source windows, and the displayed monotonicity evidence for the selected index list.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the selected windows and their rational tail budgets.
\item $E$ is the $\RealUp$ seal row reached after the regular rational readback is accepted.
\item $H$ records componentwise $\hsame$ transports for $K,B,S,W,R,E$.
\item $C$ records displayed $\Cont$ replays from compact-metric source reads to stream windows, Baire cylinders, subsequence windows, regular rational readbacks, and the terminal real seal.
\item $P$ is the $\Pkg$ provenance over $\SequentialCompactUp$, $\CompactMetricUp$, $\BaireSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SequentialCompactUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,B,S,W,R,E,H,C,P,N$. It has no coordinate for an externally chosen subsequence, quotient equality of streams, open-cover compactness, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[SequentialCompact NameCert obligations]
\label{thm:sequential-compact-namecert-obligations}
For every accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\SequentialCompactUp}$ surface consists exactly of finite rows for carrier admission, compact-metric source exposure, Baire-cylinder exposure, stream-window inspection, subsequence-window monotonicity, regular rational readback, Real seal nonescape, componentwise transport, continuation replay, provenance, and local naming. No obligation row may be discharged by host sequential compactness, countable choice, quotient stream equality, an externally selected subsequence, or ambient Real completeness.
\end{theorem}
\leanchecked{BEDC.Derived.SequentialCompactUp.TasteGate.SequentialCompactTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is projection from \autoref{def:sequential-compact-carrier}. The accepted packet exposes exactly the compact metric source, Baire cylinder row, stream window, subsequence window, regular rational readback, Real seal, transport, continuation, provenance, and local naming rows.

The compactness and choice-sequence reads are finite. The $\CompactMetricUp$ row supplies only displayed metric and cover data, while the $\BaireSpaceUp$ row supplies only finite cylinder access before any selected window is consumed.

The subsequence evidence is the row $W$. Its selected indices, selected source windows, and monotonicity evidence are packet data, and the $\hsame$ and $\Cont$ rows transport and replay those same data without adding a second selection source.

The readback then passes through $R$ and $E$. Since neither row has a coordinate for host sequential compactness, countable choice, quotient stream equality, an external subsequence, or ambient Real completeness, the local NameCert surface is exhausted by the displayed finite rows.
\end{proof}

\begin{theorem}[SequentialCompact obligation readiness]
\label{thm:sequential-compact-obligation-readiness}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the checked TasteGate carrier-alignment marker above makes the next obligation surface exactly the finite-window classifier exposure for $K,B,S,W,R,E,H,C,P,N$, subsequence-window monotonicity in $W$, $\RegSeqRatUp$ handoff through $R$, $\RealUp$ seal nonescape through $E$, and refusal of any host subsequence selector, quotient stream equality, countable choice, open-cover compactness theorem, or ambient Real completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.SequentialCompactUp.SequentialCompactCarrier\_obligation\_readiness}
\begin{proof}
Start from \autoref{thm:sequential-compact-namecert-obligations} and the displayed TasteGate carrier-alignment marker attached to it. The checked alignment pins the TasteGate carrier to the same tuple $K,B,S,W,R,E,H,C,P,N$ used by the paper surface.

The finite-window classifier exposure is therefore not an additional carrier. It is the componentwise classifier read of the existing compact-metric source, Baire cylinder row, stream window, subsequence window, regular readback, real seal, transport, continuation, provenance, and local naming rows.

The remaining rows are forced by dependency order. The subsequence-window monotonicity obligation is the monotonicity evidence inside $W$; the $\RegSeqRatUp$ handoff is $R$; and the terminal $\RealUp$ nonescape row is $E$.

Because none of the aligned carrier coordinates contains a host subsequence selector, quotient stream equality, countable choice, open-cover compactness theorem, or ambient real-completeness principle, those refusals are part of the exact obligation surface for the next closure step.
\end{proof}

\begin{theorem}[SequentialCompact root obligation Baire window]
\label{thm:sequential-compact-root-obligation-baire-window}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every root obligation that consumes selected finite windows must expose the $\BaireSpaceUp$ cylinder row $B$ before the selected-window row $W$. The selected indices and selected source windows remain data of $W$ inside the same $\BHist$ packet, transported by $H$, replayed by $C$, and named by $N$; they are not supplied by an external subsequence selector or by countable choice.
\end{theorem}
\begin{proof}
Start from \autoref{thm:sequential-compact-obligation-readiness}. It identifies the next obligation surface with the displayed rows $K,B,S,W,R,E,H,C,P,N$ and with the finite-window classifier exposure of those rows.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. The handoff order places the compact-metric source $K$, the Baire cylinder row $B$, and the stream-window row $S$ before the selected-window row $W$ is consumed.

The structural rows then preserve that order. Transport $H$, replay $C$, provenance $P$, and local naming $N$ keep the selected finite windows inside the displayed packet, so the root obligation cannot start from an external selector or a countable-choice schedule.
\end{proof}

\begin{theorem}[SequentialCompact root obligation Real seal]
\label{thm:sequential-compact-root-obligation-real-seal}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every root obligation that reaches the terminal $\RealUp$ seal $E$ must first consume $\RegSeqRatUp$ readback through $R$. The seal is therefore downstream of $K,B,S,W,R$ and of the structural rows $H,C,P,N$, and it cannot be used as an ambient Real-completeness theorem, selected Real limit, quotient stream equality, or host subsequence principle.
\end{theorem}
\begin{proof}
Use \autoref{thm:sequential-compact-obligation-readiness} to read the root obligation surface. The readiness theorem names $\RegSeqRatUp$ handoff through $R$ and $\RealUp$ seal nonescape through $E$ as rows of the same finite carrier.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. It routes selected finite windows through $W$ before regular rational readback in $R$ and before the terminal seal in $E$.

Finally use the existing nonescape route, including \autoref{thm:sequential-compact-real-seal-nonescape}. The row $E$ remains an endpoint of the displayed handoff, not a source of ambient completeness, selected limits, quotient equality, or host subsequence data.
\end{proof}

\begin{theorem}[SequentialCompact root obligation nonescape]
\label{thm:sequential-compact-root-obligation-nonescape}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the root obligation surface consists only of the displayed rows $K,B,S,W,R,E,H,C,P,N$. It has no row for quotient stream equality, externally selected subsequences, countable choice, open-cover compactness, selected Real limits, host sequential compactness, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the carrier and apply \autoref{thm:sequential-compact-namecert-obligations}. The local certificate surface is exactly the finite tuple $K,B,S,W,R,E,H,C,P,N$ with compact-metric source exposure, Baire-cylinder exposure, stream-window inspection, selected-window monotonicity, regular readback, Real seal nonescape, transport, replay, provenance, and local naming.

Use \autoref{thm:sequential-compact-obligation-readiness}. It states that the aligned root surface refuses host subsequence selectors, quotient stream equality, countable choice, open-cover compactness, and ambient Real completeness as obligation rows.

The finite-subsequence handoff keeps the same refusal through the downstream route. Since $H,C,P,N$ only preserve and name the displayed rows, the root obligation surface cannot export any of the excluded host or quotient principles.
\end{proof}

\begin{theorem}[SequentialCompact Baire cylinder exposure]
\label{thm:sequential-compact-baire-cylinder-exposure}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
any compact-metric completion consumer must read the $\BaireSpaceUp$ cylinder row $B$ before it reads the selected finite-window row $W$. The row $B$ is part of the same carrier surface as $K,S,W,R,E,H,C,P,N$, and the consumer may not replace it by a host choice-sequence branch, open-cover compactness theorem, countable-choice selector, quotient stream equality, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Start from \autoref{thm:sequential-compact-namecert-obligations}. The obligation surface includes Baire-cylinder exposure as a named row of the accepted packet, so $B$ is visible before any downstream read can treat selected windows as evidence.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. Its handoff order places $\BaireSpaceUp$ before $\StreamNameUp$ and before the finite subsequence-window row. Therefore a compact-metric completion consumer cannot inspect $W$ without first passing through $B$.

Finally use \autoref{thm:sequential-compact-obligation-readiness}. The readiness surface refuses host subsequence selection, quotient stream equality, countable choice, open-cover compactness, and ambient Real completeness, so the Baire exposure remains the displayed finite cylinder row.
\end{proof}

\begin{theorem}[SequentialCompact window transport]
\label{thm:sequential-compact-window-transport}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the componentwise $\hsame$ transport row $H$ preserves the source stream row $S$, selected-window row $W$, regular readback row $R$, and terminal seal row $E$ before any completion consumer reads the route. Transport cannot introduce a second selector, quotient stream equality, countable-choice witness, open-cover compactness theorem, or ambient real-completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:sequential-compact-carrier}. The row $H$ records componentwise transport exactly for the displayed analytic rows $K,B,S,W,R,E$.

Use \autoref{thm:sequential-compact-namecert-obligations} to identify the local certificate surface. Transport is one of its structural rows and acts on the existing carrier coordinates rather than on a hidden host sequence.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. Since $S,W,R,E$ are read in that order by completion consumers, the transported route preserves the same order and exports none of the excluded host principles.
\end{proof}

\begin{theorem}[SequentialCompact selector refusal]
\label{thm:sequential-compact-selector-refusal}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
there is no row naming a host subsequence selection function, countable-choice principle, quotient stream equality, or open-cover compactness theorem. Every selected-window read is the displayed finite row $W$ after the compact-metric source row $K$, Baire cylinder row $B$, and stream-window row $S$ have been exposed.
\end{theorem}
\begin{proof}
Begin with the carrier definition. The tuple contains $W$ as finite selected-window data, but it contains no coordinate for a host selector, countable-choice object, quotient stream equality, or open-cover compactness theorem.

Apply \autoref{thm:sequential-compact-namecert-obligations}. The local NameCert surface is exhausted by the displayed rows $K,B,S,W,R,E,H,C,P,N$, so no additional selector row can be supplied by the certificate.

Finally use \autoref{thm:sequential-compact-finite-subsequence-handoff}. Any completion-facing consumer reaches $W$ only through the finite handoff order, and the subsequent readback and seal rows preserve that refusal.
\end{proof}

\begin{theorem}[SequentialCompact finite subsequence handoff]
\label{thm:sequential-compact-finite-subsequence-handoff}
Every accepted $\SequentialCompactUp$ packet consumed by a compact-metric or Baire-space completion route must expose the finite handoff
$$
\CompactMetricUp,\quad \BaireSpaceUp,\quad \StreamNameUp,\quad \RegSeqRatUp,\quad \RealUp
$$
in that order: compact source data and Baire cylinder data are read before stream windows, stream windows are read before the displayed subsequence-window row, and the selected windows are read before the regular rational handoff and Real seal. The handoff exports no host subsequence selector, quotient stream equality, open-cover compactness theorem, countable choice, or ambient Real completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.SequentialCompactUp.SequentialCompactCarrier\_finite\_subsequence\_handoff}
\begin{proof}
Project the carrier $Q=(K,B,S,W,R,E,H,C,P,N)$. The rows $K$ and $B$ are the only compact-metric and Baire-space sources available to the consumer.

Next read the stream and subsequence windows. The row $S$ gives finite source-window access, and the row $W$ gives the selected finite windows and monotonicity evidence over those source windows.

Finally apply the readback and seal rows. The row $R$ consumes only the selected windows from $W$, and the row $E$ seals only the accepted regular rational readback. The transport, continuation, provenance, and NameCert rows preserve this same handoff, so no host subsequence selector, quotient stream equality, open-cover compactness theorem, countable choice, or ambient Real completeness can be exported.
\end{proof}

\begin{theorem}[SequentialCompact RegSeqRat readback route]
\label{thm:sequential-compact-regseqrat-readback-route}
Any accepted $\SequentialCompactUp$ packet that reaches the terminal $\RealUp$ seal must first expose the selected finite windows in $W$ and then the regular rational readback row $R$. No consumer may replace $R$ by a host subsequence limit, quotient stream equality, countable-choice selector, open-cover compactness theorem, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start from the NameCert obligations, \autoref{thm:sequential-compact-namecert-obligations}. They identify $W$ and $R$ as displayed carrier rows, not as hidden host selectors or quotient-stream data.

Apply the finite subsequence handoff, \autoref{thm:sequential-compact-finite-subsequence-handoff}. It orders the completion-facing route so that selected windows are exposed before regular rational readback and before the terminal RealUp seal.

Use window transport and selector refusal, \autoref{thm:sequential-compact-window-transport} and \autoref{thm:sequential-compact-selector-refusal}. Transport preserves the displayed rows, while the refusal theorem leaves no coordinate for a host subsequence limit, quotient stream equality, countable-choice selector, open-cover compactness theorem, or ambient completeness principle.
\end{proof}

\begin{theorem}[SequentialCompact selector monotonicity]
\label{thm:sequential-compact-selector-monotonicity}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the selected finite windows exposed to any compact-metric or Baire-space completion consumer are monotone exactly because the row $W$ displays the selected index list, the selected source windows, and the monotonicity evidence for that list. No consumer may replace $W$ by an externally selected subsequence, countable-choice function, quotient stream selector, or host sequential compactness theorem.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:sequential-compact-carrier}. The only coordinate that stores selected windows is $W$, and its displayed data include the selected indices, selected source windows, and monotonicity evidence.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. Any completion consumer reads $K,B,S$ before it reaches $W$, and the subsequent rows $R,E,H,C,P,N$ preserve the same finite handoff.

Thus selector monotonicity is not imported from a host choice principle. It is the projection of the finite row $W$, transported by $H$ and replayed by $C$ without adding any second selector coordinate.
\end{proof}

\begin{theorem}[SequentialCompact RegSeqRat handoff exactness]
\label{thm:sequential-compact-regseqrat-handoff-exactness}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the row $R$ is the only $\RegSeqRatUp$ handoff available after the finite subsequence-window row $W$ has been displayed. Every rational-tail budget, regular readback, or downstream completion request that depends on selected windows must pass through $R$ before it can reach the terminal $\RealUp$ seal $E$.
\end{theorem}
\begin{proof}
Read the handoff order in \autoref{thm:sequential-compact-finite-subsequence-handoff}. The route reaches $\StreamNameUp$ through $S$, then the selected finite windows through $W$, and only then the regular rational readback through $R$.

The carrier has no alternate regular rational coordinate. The rows $H$ and $C$ can transport and replay $R$, while $P$ and $N$ record provenance and naming for the same displayed row.

Consequently exactness of the $\RegSeqRatUp$ handoff is a projection claim about $R$. A consumer that asks for rational-tail data after $W$ receives that row and cannot bypass it through quotient stream equality, a selected limit, or ambient completeness.
\end{proof}

\begin{theorem}[SequentialCompact Real seal nonescape]
\label{thm:sequential-compact-real-seal-nonescape}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the terminal $\RealUp$ row $E$ is reachable only after the compact metric source $K$, Baire cylinder row $B$, stream-window row $S$, subsequence-window row $W$, regular rational handoff $R$, and structural rows $H,C,P,N$ have been displayed. The seal exports no ambient Real completeness, selected limit, quotient equality of streams, countable choice, or host sequential compactness theorem.
\end{theorem}
\begin{proof}
Start with the carrier projection. The row $E$ is listed after $R$ and is described as the $\RealUp$ seal reached after the regular rational readback is accepted.

Use \autoref{thm:sequential-compact-selector-monotonicity} to keep the selected finite windows inside $W$. Then use \autoref{thm:sequential-compact-regseqrat-handoff-exactness} to force every rational-tail read from those windows through $R$.

It remains only to inspect the structural rows. Transport, replay, provenance, and naming preserve the displayed route $K,B,S,W,R,E$; they do not add completeness, quotient, or choice coordinates. Hence the real seal is a nonescaping endpoint of the finite handoff, not an ambient Real-completeness principle.
\end{proof}

\begin{theorem}[SequentialCompact window extraction scope]
\label{thm:sequential-compact-window-extraction-scope}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every finite extraction request must expose the compact metric source row $K$, the Baire cylinder row $B$, the stream-window row $S$, and the selected finite-window row $W$ before any $\RegSeqRatUp$ readback or terminal $\RealUp$ seal is available. The extraction scope exports no host subsequence selector, countable choice, quotient stream equality, open-cover compactness theorem, selected Real limit, or ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:sequential-compact-baire-cylinder-exposure}. It places the Baire cylinder row $B$ before selected-window data can be consumed, so an extraction request cannot start from a detached selector.

Next apply \autoref{thm:sequential-compact-finite-subsequence-handoff}. The route reads $K,B,S,W$ in finite order, and the selected source windows are packet rows rather than an infinite subsequence object.

Use \autoref{thm:sequential-compact-selector-monotonicity}. It keeps the selected indices and selected windows inside $W$, while $H,C,P,N$ only transport, replay, source, and name the same displayed rows.

The later rows $R$ and $E$ are downstream of the window route. Hence the extraction scope is finite and does not export the excluded host selector, choice, quotient, compactness, selected-limit, or completeness principles.
\end{proof}

\begin{theorem}[SequentialCompact Baire RegSeqRat exhaustion]
\label{thm:sequential-compact-baire-regseqrat-exhaustion}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every regular rational readback requested after a Baire cylinder exposure must pass through the row $R$. The request first displays $B$, then the stream and selected-window rows $S,W$, and only then reads $R$ before the seal $E$; no host subsequence selector, countable choice, quotient stream equality, open-cover compactness theorem, or ambient Real completeness is exported.
\end{theorem}
\begin{proof}
Read the Baire exposure through \autoref{thm:sequential-compact-baire-cylinder-exposure}. It supplies the cylinder row $B$ as displayed finite data before selected windows are available.

Apply \autoref{thm:sequential-compact-window-extraction-scope}. The request reaches the selected windows through $K,B,S,W$, so the regular rational readback is tied to the same finite route.

Now use \autoref{thm:sequential-compact-regseqrat-handoff-exactness}. It identifies $R$ as the only $\RegSeqRatUp$ handoff after $W$, and the structural rows do not add another readback coordinate.

Therefore the Baire-to-RegSeqRat route is exhausted by $B,S,W,R$ and cannot be replaced by a host selector, a choice schedule, quotient stream equality, open-cover compactness, or ambient completeness.
\end{proof}

\begin{theorem}[SequentialCompact Real seal window nonescape]
\label{thm:sequential-compact-real-seal-window-nonescape}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
the terminal $\RealUp$ seal $E$ is a window endpoint: it may be read only after the Baire cylinder row $B$, stream-window row $S$, selected-window row $W$, and regular rational readback row $R$ have been displayed. The seal exports no host subsequence selector, countable choice, quotient stream equality, open-cover compactness theorem, selected Real limit, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:sequential-compact-window-extraction-scope}. It forces every extraction request to expose $B,S,W$ as finite packet rows before downstream readback can begin.

Then apply \autoref{thm:sequential-compact-baire-regseqrat-exhaustion}. Every regular rational request after that exposure passes through $R$, so the seal cannot be reached from a detached stream or selector.

Finally use \autoref{thm:sequential-compact-real-seal-nonescape}. The row $E$ is downstream of $R$ and of the structural rows $H,C,P,N$, all of which preserve the displayed route.

Thus the Real seal remains a finite-window endpoint. It does not provide a host subsequence selector, countable choice, quotient stream equality, open-cover compactness, selected Real limit, or ambient completeness.
\end{proof}

\begin{theorem}[SequentialCompact cylinder monotone window]
\label{thm:sequential-compact-cylinder-monotone-window}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every $\BaireSpaceUp$ cylinder exposure consumed by a compact-metric or Baire-space route is tied to the monotone selected-window row $W$. The consumer may inspect $B$ and then $W$, transported by $H$ and replayed by $C$, but it may not replace that route by a host choice-sequence branch, a nonmonotone selector, quotient stream equality, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the Baire exposure theorem \autoref{thm:sequential-compact-baire-cylinder-exposure}. It places the cylinder row $B$ before any downstream read of selected windows, so the consumer reaches the window surface through the displayed carrier order.

Apply \autoref{thm:sequential-compact-finite-subsequence-handoff} and \autoref{thm:sequential-compact-selector-monotonicity}. The handoff places $W$ after $K,B,S$, and the selector monotonicity theorem identifies the monotone selected indices and selected source windows as data stored inside $W$.

Finally use \autoref{thm:sequential-compact-real-seal-nonescape}. The later readback and seal rows preserve the same finite route, so no consumer can bypass the Baire cylinder and monotone selected-window boundary through a host selector or an ambient compactness principle.
\end{proof}

\begin{theorem}[SequentialCompact regular tail nonescape]
\label{thm:sequential-compact-regular-tail-nonescape}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every tail request made after the selected finite-window row $W$ must pass through the $\RegSeqRatUp$ row $R$ before it can reach the terminal $\RealUp$ seal row $E$. The request exports no quotient stream equality, selected limit, countable-choice schedule, host sequential compactness theorem, open-cover compactness theorem, or ambient Real completeness row.
\end{theorem}
\begin{proof}
Read $W$ through \autoref{thm:sequential-compact-selector-monotonicity}. The selected finite windows and their monotonicity evidence are packet data, not a host subsequence object.

Next apply \autoref{thm:sequential-compact-regseqrat-handoff-exactness}. It identifies $R$ as the only regular rational handoff available after $W$, so every rational-tail budget or regular readback request must use that row.

Now apply \autoref{thm:sequential-compact-real-seal-nonescape}. The seal row $E$ is reachable only after $R$ and the structural rows have been displayed, hence the tail request cannot escape through quotient streams, selected limits, countable choice, host compactness, or ambient completeness.
\end{proof}

\begin{theorem}[SequentialCompact Real seal consumer boundary]
\label{thm:sequential-compact-real-seal-consumer-boundary}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every compact-metric, Baire-space, regular-rational, stream-window, or Real-facing consumer of the terminal seal can inspect only the rows $K,B,S,W,R,E,H,C,P,N$. In particular, the consumer sees no row for external subsequence selection, quotient stream equality, open-cover compactness, countable choice, selected Real limits, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:sequential-compact-carrier}. Its visible coordinates are exactly $K,B,S,W,R,E,H,C,P,N$, and the local NameCert obligation theorem identifies those rows as the certificate surface.

Use \autoref{thm:sequential-compact-finite-subsequence-handoff} for the consumer order. Compact-metric and Baire reads pass through $K$ and $B$, stream-window reads pass through $S$ and $W$, regular rational reads pass through $R$, and the Real-facing endpoint is $E$.

Finally combine \autoref{thm:sequential-compact-regseqrat-handoff-exactness} with \autoref{thm:sequential-compact-real-seal-nonescape}. They force the regular tail through $R$ and the Real seal through $E$, while the structural rows preserve the displayed route and do not add excluded host or quotient data.
\end{proof}

\begin{theorem}[SequentialCompact finite subsequence obligation]
\label{thm:sequentialcompact-finite-subsequence-obligation}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every finite subsequence obligation read from $Q$ is a $\BHist$ obligation over the displayed rows $K,B,S,W,R,E,H,C,P,N$. The selected-window row $W$ must be transported by the componentwise $\hsame$ row $H$, replayed through the displayed $\Cont$ row $C$, and named by the local $\NameCert_{\SequentialCompactUp}$ row $N$ before any compact-metric, stream-window, regular-rational, or Real-facing consumer can use it. The obligation refuses host subsequence selectors, countable choice, quotient stream equality, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier from \autoref{def:sequential-compact-carrier}. The only row that stores selected subsequence information is $W$, and the carrier records it as finite selected indices, selected source windows, and monotonicity evidence.

Use \autoref{thm:sequential-compact-finite-subsequence-handoff}. The handoff forces the consumer to reach $W$ only after the compact-metric, Baire-cylinder, and stream-window rows have been displayed.

Now read the structural rows. The $\hsame$ row $H$ transports the selected-window data componentwise, the $\Cont$ row $C$ replays the same finite route, and the local $\NameCert$ row $N$ names that displayed packet. None of these rows contains a coordinate for a host selector, countable-choice schedule, quotient stream equality, or ambient Real completeness.
\end{proof}

\begin{theorem}[SequentialCompact cluster carrier stability]
\label{thm:sequentialcompact-cluster-carrier-stability}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
any cluster-window read exposed by $Q$ is stable only along the same $\BHist$ carrier tuple. If a consumer changes presentation through $\hsame$, the cluster read remains the transported $W,R,E$ route replayed by $\Cont$ and named by $\NameCert_{\SequentialCompactUp}$; it does not become a host subsequence selector, a countable-choice witness, a quotient stream equality, or an ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with \autoref{thm:sequential-compact-window-transport}. The row $H$ preserves the stream-window, selected-window, regular-readback, and terminal-seal rows before any completion consumer reads the route.

The cluster read is therefore carrier-local. It can use $W$ for selected finite windows, $R$ for regular rational readback, and $E$ for the terminal seal, but each of these rows remains inside the same tuple $Q$.

Finally apply \autoref{thm:sequential-compact-real-seal-consumer-boundary}. A Real-facing or compact-metric consumer can inspect only $K,B,S,W,R,E,H,C,P,N$, so no presentation change can export the excluded host selector, choice, quotient, or ambient completeness data.
\end{proof}

\begin{theorem}[SequentialCompact compactmetric consumer scope]
\label{thm:sequentialcompact-compactmetric-consumer-scope}
For an accepted $\SequentialCompactUp$ carrier
$$
Q=(K,B,S,W,R,E,H,C,P,N),
$$
every $\CompactMetricUp$ consumer that uses the sequential-compactness packet has scope exactly the finite $\BHist$ rows $K,B,S,W,R,E,H,C,P,N$. It may read compact-metric source data, Baire cylinders, stream windows, finite subsequence windows, regular rational readback, the Real seal, $\hsame$ transport, $\Cont$ replay, package provenance, and the local $\NameCert$ row, but it may not request host subsequence selectors, countable choice, quotient stream equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the compact-metric source through $K$. The carrier definition gives no other compactness coordinate, and \autoref{thm:sequential-compact-baire-cylinder-exposure} places the Baire row $B$ before selected windows are consumed.

Next use \autoref{thm:sequentialcompact-finite-subsequence-obligation}. It binds the finite subsequence obligation to $W,H,C,N$, so the compact-metric consumer receives displayed packet data rather than an external selector.

The downstream rows are $R$ and $E$. By \autoref{thm:sequential-compact-regseqrat-handoff-exactness} and \autoref{thm:sequential-compact-real-seal-nonescape}, those rows provide regular readback and the terminal seal without exporting quotient stream equality, countable choice, host subsequence selection, or ambient Real completeness.
\end{proof}

\closureat{SequentialCompactUp}{seedStr}

\begin{closurestatus}{\SequentialCompactUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sequential-compact-carrier}, \autoref{thm:sequential-compact-namecert-obligations}, and \autoref{thm:sequential-compact-finite-subsequence-handoff} seed the finite subsequence-window boundary for compact-metric and Baire-space completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host sequential compactness, countable choice, quotient stream equality, open-cover compactness, external subsequence selection, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window classifier exposure, subsequence-window monotonicity, RegSeqRat handoff exactness, RealUp seal nonescape, and selector-refusal proofs for BEDC.Derived.SequentialCompactUp.}
  \constructivestory{A $\SequentialCompactUp$ packet is generated from CompactMetric source data, BaireSpace cylinder data, StreamName source windows, displayed finite subsequence windows, RegSeqRat readback, Real seal, componentwise transport, continuation replay, provenance, and a local NameCert row.}
\end{closurestatus}
