\chapter{A Concrete Naming Certificate for $\RealNullSequenceUp$}
\label{ch:concrete-instances-real-null-sequence-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealNullSequenceUp$ packet records a displayed real-valued sequence whose finite convergence surface is tied to the zero $\RealUp$ row. It sits after the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the displayed sequence-limit interface of \autoref{ch:concrete-instances-real-sequence-limit-namecert}. The packet gives later sequence-algebra and Cauchy-criterion consumers a finite zero-limit route without importing host sequence equality, quotient limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[RealNullSequence carrier]
\label{def:real-null-sequence-carrier}
A $\RealNullSequenceUp$ carrier is a finite $\BHist$ packet
$$
Z=(S,0,W,R,D,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is a displayed sequence of $\RealUp$ names, each read only through the finite packet rows made visible to this carrier.
\item $0$ is the displayed zero $\RealUp$ row, supplied as the candidate limit and not as a host-level constant outside the packet.
\item $W$ stores the $\StreamNameUp$ finite windows used to inspect sequence entries and the zero row at the requested tolerances.
\item $R$ stores the $\RegSeqRatUp$ readback rows attached to those windows.
\item $D$ stores the $\DyadicRatCoreUp$ tolerances, slack rows, and comparison budgets used by every scheduled read.
\item $L$ is the $\RealSequenceLimitUp$ convergence classifier row, specialized to the displayed sequence $S$ and the zero row $0$.
\item $H$ records componentwise $\hsame$ transport for sequence rows, zero row, windows, readbacks, tolerances, convergence classifier, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from sequence windows through regular rational readback, dyadic tolerance comparison, and the zero-limit classifier.
\item $P$ is the $\Pkg$ provenance over $\RealNullSequenceUp$, $\RealSequenceLimitUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RealNullSequenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,0,W,R,D,L,H,C,P,N$. It has no coordinate for host sequence equality, quotient limits, countable-choice schedules, trichotomy decisions, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RealNullSequence NameCert obligations]
\label{thm:real-null-sequence-namecert-obligations}
For every accepted $\RealNullSequenceUp$ carrier $Z=(S,0,W,R,D,L,H,C,P,N)$, the local $\NameCert_{\RealNullSequenceUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed $\RealUp$ sequence row, zero $\RealUp$ row, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ tolerances, $\RealSequenceLimitUp$ classifier, transport, replay, provenance, and local naming rows;
\item zero-row exposure, requiring every accepted limit read to expose the displayed zero $\RealUp$ row before the sequence-limit classifier is consumed;
\item finite-window convergence, requiring all convergence evidence to pass through the scheduled $W,R,D,L$ rows;
\item transport and replay stability, requiring $\hsame$ transport and $\Cont$ replay to preserve the same sequence, zero, window, readback, tolerance, and classifier rows;
\item refusal of host sequence equality, quotient limits, countable choice, trichotomy, and ambient completeness as packet coordinates.
\end{enumerate}
No zero-limit obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-null-sequence-carrier}. The accepted packet displays exactly the sequence row, zero row, finite windows, regular readbacks, dyadic tolerances, convergence classifier, transport, replay, provenance, and local name.

The analytic read is then forced by the row order. The sequence row $S$ and zero row $0$ are inspected only through the scheduled windows $W$, readbacks $R$, and tolerance ledger $D$, and the convergence classifier $L$ is the only row that can certify approach to the displayed zero.

Transport and replay stability follow from the structural rows $H$ and $C$. They preserve the same displayed rows componentwise and replay the same finite route before the local name is consumed.

Finally inspect the carrier inventory. Since host sequence equality, quotient limits, countable choice, trichotomy, and ambient $\RealUp$ completeness are not coordinates of $Z$, none can become a local NameCert obligation.
\end{proof}

\closureat{RealNullSequenceUp}{seedStr}

\begin{closurestatus}{\RealNullSequenceUp}
  \constructivestory{A $\RealNullSequenceUp$ packet is generated from a displayed RealUp sequence, a zero RealUp row, finite StreamName windows, RegSeqRat readbacks, DyadicRatCore tolerances, a RealSequenceLimit convergence classifier, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-null-sequence-carrier} and \autoref{thm:real-null-sequence-namecert-obligations} seed the finite zero-limit route for displayed real sequences.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close sequence algebra, Cauchy criteria, quotient limits, host sequence equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, zero-row exposure, finite-window convergence, transport stability, replay stability, and refusal rows for BEDC.Derived.RealNullSequenceUp.}
\end{closurestatus}
