\chapter{A Concrete Naming Certificate for $\BlaschkeSelectionCompactHyperspaceUp$}
\label{ch:concrete-instances-blaschke-selection-compact-hyperspace-namecert}
\origin{human}

Following Blaschke and Kelley, the $\BlaschkeSelectionCompactHyperspaceUp$ packet names the finite selection surface for a sequence of compact subsets of a compact metric source. It sits over the compact-subset ledger of \autoref{ch:concrete-instances-hyperspace-namecert}, the finite-net distance interface of \autoref{ch:concrete-instances-hausdorff-metric-namecert}, the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the directed convergence route of \autoref{ch:concrete-instances-netconvergence-namecert}, and the uniform Cauchy-net boundary of \autoref{ch:concrete-instances-cauchy-uniform-net-namecert}. The packet records finite Hausdorff-distance selection data; it is not a host compactness theorem, an open-cover argument, an ambient powerset quotient, a choice-selected subnet, or an external sequential compactness principle.

\begin{definition}[Blaschke selection compact-hyperspace carrier]
\label{def:blaschke-selection-compact-hyperspace-carrier}
A $\BlaschkeSelectionCompactHyperspaceUp$ carrier is a finite $\BHist$ packet
$$
B=(X,S,D,W,E,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the compact metric source row, including its $\MetricUp$, $\CompactMetricUp$, finite-net, total-boundedness, and completeness witnesses.
\item $S$ is the sequence of compact-subset $\HyperspaceUp$ rows over $X$, with each compact-subset presentation read only through the displayed hyperspace carrier.
\item $D$ is the $\HausdorffMetricUp$ distance-ledger family comparing the compact-subset rows of $S$ at each requested finite resolution.
\item $W$ is the finite Cauchy-subnet window ledger, recording the selected index window, cofinality evidence, Hausdorff-distance requests, and stabilization bounds.
\item $E$ is the extracted compact-subset endpoint row, displayed as a $\HyperspaceUp$ compact-subset name over the same source $X$.
\item $R$ is the dyadic and $\RealUp$ tolerance readback showing that the window ledgers in $W$ and the endpoint row $E$ answer the same finite Hausdorff-distance requests.
\item $H$ records componentwise $\hsame$ transport for the compact metric source, compact-subset sequence, Hausdorff distance ledgers, Cauchy-subnet windows, endpoint row, tolerance readback, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
X,S,D \longmapsto W \longmapsto E,R .
$$
\item $P$ is the $\Pkg$ provenance over $\BlaschkeSelectionCompactHyperspaceUp$, $\HyperspaceUp$, $\HausdorffMetricUp$, $\CompactMetricUp$, $\NetConvergenceUp$, $\CauchyUniformNetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BlaschkeSelectionCompactHyperspaceUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through $X,S,D,W,E,R,H,C,P,N$. It has no coordinate for open-cover compactness, host powersets, quotient subset equality, selected choice functions, or an unbounded subnet object.
\end{definition}

\begin{theorem}[Blaschke selection compact-hyperspace NameCert obligations]
\label{thm:blaschke-selection-compact-hyperspace-namecert-obligations}
For every accepted $\BlaschkeSelectionCompactHyperspaceUp$ carrier
$$
B=(X,S,D,W,E,R,H,C,P,N),
$$
the local $\NameCert_{\BlaschkeSelectionCompactHyperspaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the compact metric source row $X$, the compact-subset sequence $S$, the HausdorffMetric distance ledgers $D$, the finite Cauchy-subnet windows $W$, the endpoint row $E$, tolerance readback $R$, transport, replay, provenance, and local naming rows;
\item compact-subset sequence exactness, requiring every displayed member of $S$ to be admitted through $\HyperspaceUp$ over the same compact metric source $X$ before any selection window can inspect it;
\item finite Hausdorff Cauchy-window stability, requiring the ledgers in $D$ and $W$ to share the same finite resolution requests and to route their distance reads through $\HausdorffMetricUp$;
\item endpoint readback stability, requiring $E$ and $R$ to expose the selected compact-subset endpoint only by the displayed $\RealUp$ tolerance comparisons and componentwise $\hsame$ transport;
\item provenance and name exhaustion, requiring $C,P,N$ to replay, source, and name only the displayed finite route and to export no host compactness theorem, powerset quotient, selected choice function, open-cover proof, or unbounded subnet object.
\end{enumerate}
No Blaschke selection compact-hyperspace obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:blaschke-selection-compact-hyperspace-carrier}. The packet displays the compact metric source, compact-subset sequence, Hausdorff distance ledgers, Cauchy-subnet windows, endpoint row, tolerance readback, transports, replay, provenance, and local naming row as its only coordinates.

The compact-subset sequence is exact because every member of $S$ is read through the $\HyperspaceUp$ surface over the same source $X$. The Hausdorff reads are exact because $D$ records only finite $\HausdorffMetricUp$ ledgers attached to those displayed compact-subset names.

The selection step is the finite-net replay through $W$. Each selected window exposes a cofinal finite index range and a stabilization ledger, and the route through $\NetConvergenceUp$ and $\CauchyUniformNetUp$ keeps the window evidence inside displayed convergence data.

The endpoint and tolerance readback are then projected through $E$ and $R$. The endpoint is a compact-subset row over $X$, while the $\RealUp$ readback states exactly the finite Hausdorff-distance tolerances checked by the window ledgers.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed route. Since the carrier has no coordinate for host compactness, powerset quotients, choice-selected functions, open-cover proofs, or unbounded subnet objects, the five listed obligation rows exhaust the local NameCert surface.
\end{proof}

\closureat{BlaschkeSelectionCompactHyperspaceUp}{seedStr}

\begin{closurestatus}{\BlaschkeSelectionCompactHyperspaceUp}
  \constructivestory{A $\BlaschkeSelectionCompactHyperspaceUp$ packet is generated from a CompactMetricUp source, a sequence of HyperspaceUp compact-subset rows, HausdorffMetricUp distance ledgers, finite Cauchy-subnet windows, an endpoint compact-subset row, RealUp tolerance readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:blaschke-selection-compact-hyperspace-carrier} and \autoref{thm:blaschke-selection-compact-hyperspace-namecert-obligations} seed the finite compact-hyperspace selection surface through Hyperspace, HausdorffMetric, CompactMetric, NetConvergence, and CauchyUniformNet rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host compactness, open-cover compactness, powerset quotients, choice-selected functions, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-subset sequence exactness, finite Hausdorff Cauchy-window stability, endpoint readback stability, and provenance/name exhaustion for BEDC.Derived.BlaschkeSelectionCompactHyperspaceUp.}
\end{closurestatus}
