\chapter{A Concrete Naming Certificate for $\FanModulusBoundaryUp$}
\label{ch:concrete-instances-fan-modulus-boundary-namecert}
\origin{human}

Following Brouwer's fan theorem and Bishop--Bridges constructive analysis, the $\FanModulusBoundaryUp$ packet records the boundary at which a finite fan-bar depth becomes a compact-uniform-continuity modulus handoff. It sits over the finite bar packet of \autoref{ch:concrete-instances-fantheorem-namecert}, the bar-to-window schedule of \autoref{ch:concrete-instances-bishop-fan-modulus-namecert}, the compact-uniform-continuity consumer of \autoref{ch:concrete-instances-compactuniformcontinuity-namecert}, and the uniform-modulus surface of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet uses $\mathsf{ProbeBundle}$ routes for finite branch windows and finite compact-source probes; it is not open-cover compactness, not countable choice, not a selected branch, and not $\RealUp$ completeness.

\begin{definition}[Fan modulus boundary carrier]
\label{def:fan-modulus-boundary-carrier}
A $\FanModulusBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(F,M,W,Q,U,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FanTheoremUp$ row, recording the binary fan, decidable bar classifier, finite depth ledger, and finite branch-prefix witness window.
\item $M$ is the $\BishopFanModulusUp$ row, exposing the bar-depth-to-window-modulus schedule through StreamName, RegSeqRat, DyadicRatCore, and Real readback rows.
\item $W$ is the boundary-window row. It records the finite branch-prefix window that may be handed to compact-uniform-continuity consumers without selecting an infinite branch.
\item $Q$ is the $\mathsf{ProbeBundle}$ route row, aligning finite fan-prefix probes with the compact finite-net probes used by the compact-uniform-continuity source.
\item $U$ is the $\UniformModulusUp$ consumer row, recording the tolerance-only modulus schedule exported from the finite fan-bar boundary.
\item $R$ is the $\CompactUniformContinuityUp$ readback row, recording that the exported modulus is consumed only as a compact finite-net and pointwise-modulus handoff.
\item $H$ records componentwise $\hsame$ transport for the fan row, Bishop fan modulus row, boundary window, ProbeBundle route, UniformModulus row, compact-uniform readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
F,M,W,Q \longmapsto U \longmapsto R .
$$
\item $P$ is the $\Pkg$ provenance over $\FanModulusBoundaryUp$, $\FanTheoremUp$, $\BishopFanModulusUp$, $\CompactUniformContinuityUp$, $\UniformModulusUp$, $\ProbeBundle$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FanModulusBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,M,W,Q,U,R,H,C,P,N$. It has no coordinate for open-cover compactness, countable choice, selected branches, selected limits, quotient stream equality, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[FanModulusBoundaryUp NameCert obligations]
\label{thm:fan-modulus-boundary-namecert-obligations}
For every accepted $\FanModulusBoundaryUp$ carrier
$$
B=(F,M,W,Q,U,R,H,C,P,N),
$$
the local $\NameCert_{\FanModulusBoundaryUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the finite fan row, Bishop fan modulus row, boundary window, ProbeBundle route, UniformModulus consumer, compact-uniform readback, transport, replay, provenance, and local naming rows;
\item fan-bar depth exactness, requiring every finite depth used by $W$ to be read through the displayed $\FanTheoremUp$ bar classifier and witness window;
\item Bishop modulus boundary exactness, requiring the window schedule in $M$ to be the only Real and Completion-facing modulus source exposed to $U$;
\item ProbeBundle compatibility, requiring $Q$ to align finite fan-prefix probes with compact finite-net probes before the compact-uniform-continuity readback $R$ is public;
\item $\hsame$ and $\Cont$ transport through $H$ and $C$, preserving the same fan-bar, modulus, ProbeBundle, UniformModulus, and compact-uniform rows under replay;
\item ledger nonescape through $P$ and $N$, excluding open-cover compactness, countable choice, selected branches, selected limits, quotient stream equality, host real equality, and ambient $\RealUp$ completeness.
\end{enumerate}
No fan modulus boundary obligation is stored outside these rows.
\end{theorem}

\closureat{FanModulusBoundaryUp}{seedStr}

\begin{closurestatus}{\FanModulusBoundaryUp}
  \constructivestory{A $\FanModulusBoundaryUp$ packet is generated from a FanTheoremUp finite bar row, BishopFanModulusUp bar-to-window schedule, finite boundary windows, ProbeBundle compatibility, UniformModulus handoff, CompactUniformContinuity readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fan-modulus-boundary-carrier} and \autoref{thm:fan-modulus-boundary-namecert-obligations} seed the finite fan-bar modulus boundary consumed by compact-uniform-continuity and UniformModulus rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, countable choice, selected branches, selected limits, quotient stream equality, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, fan-bar depth exactness, Bishop modulus boundary exactness, ProbeBundle compatibility, UniformModulus handoff, compact-uniform readback, transport, replay, provenance, local naming, and ledger nonescape for BEDC.Derived.FanModulusBoundaryUp.}
\end{closurestatus}
