\chapter{A Concrete Naming Certificate for $\CauchyCondensationRealSeriesUp$}
\label{ch:concrete-instances-cauchy-condensation-real-series-namecert}
\origin{human}

Following Cauchy and Bishop--Bridges constructive analysis, the $\CauchyCondensationRealSeriesUp$ packet names the finite tail-comparison route for positive decreasing $\RealSeriesUp$ terms. It sits next to the real-series surface of \autoref{ch:concrete-instances-realseries-namecert}, the displayed limit interface of \autoref{ch:concrete-instances-real-sequence-limit-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. It refines the dyadic-block test packet of \autoref{ch:concrete-instances-cauchy-condensation-test-namecert} by making the $\RealSeriesUp$ tail carrier itself visible to Real and Completion consumers before any infinite sum or completed endpoint is read.

\begin{definition}[CauchyCondensationRealSeries carrier]
\label{def:cauchy-condensation-real-series-carrier}
A $\CauchyCondensationRealSeriesUp$ carrier is a finite $\BHist$ packet
$$
K=(A,M,B,G,W,Q,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the positive decreasing $\RealSeriesUp$ source row. Its terms are admitted only through finite term windows, and its decreasing evidence is read as adjacent finite comparisons.
\item $M$ is the monotone-tail ledger, recording positivity, decreasing transport, and the finite tail cut from which the comparison begins.
\item $B$ is the dyadic block-window ledger. It lists the inspected powers of two, the associated block endpoints, and the finite intervals of original terms visible at each requested tolerance.
\item $G$ is the condensed-term row, displaying the term $2^n a_{2^n}$ on the same dyadic indices as $B$ and tying it to the original $\RealSeriesUp$ term windows.
\item $W$ is the $\StreamNameUp$ schedule used for the original terms, block endpoints, condensed terms, and partial-sum windows.
\item $Q$ is the $\RegSeqRatUp$ readback row for every displayed original term, condensed term, and block partial sum.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and block-comparison ledger. It records the finite inequalities that bound each inspected original tail block above and below by the matching condensed-term rows.
\item $R$ is the $\RealSequenceLimitUp$ route for the partial-sum and condensed-partial-sum windows that the packet exposes to downstream limit consumers.
\item $E$ is the $\RealUp$ seal row reached only after $A,M,B,G,W,Q,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source, monotone-tail ledger, dyadic blocks, condensed terms, schedules, readbacks, tolerance ledger, limit route, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tail request through the monotone ledger, dyadic blocks, condensed terms, stream schedules, regular readbacks, dyadic comparisons, limit route, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyCondensationRealSeriesUp$, $\RealSeriesUp$, $\RealSequenceLimitUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCondensationRealSeriesUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,M,B,G,W,Q,D,R,E,H,C,P,N$. It has no coordinate for host infinite sums, quotient real equality, countable choice, trichotomy, selected endpoints, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CauchyCondensationRealSeries obligations]
\label{thm:cauchy-condensation-real-series-obligations}
For every accepted $\CauchyCondensationRealSeriesUp$ carrier $K=(A,M,B,G,W,Q,D,R,E,H,C,P,N)$, the local $\NameCert_{\CauchyCondensationRealSeriesUp}$ surface consists exactly of carrier admission for the displayed thirteen-row packet; positive decreasing $\RealSeriesUp$ source exposure through $A$ and $M$; dyadic block-window coverage through $B$; condensed-term formation through $G$; $\StreamNameUp$ scheduling through $W$; $\RegSeqRatUp$ readback through $Q$; $\DyadicRatCoreUp$ block comparison through $D$; $\RealSequenceLimitUp$ partial-sum routing through $R$; $\RealUp$ sealing through $E$; componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-condensation-real-series-carrier}. The accepted packet exposes exactly the source, monotone-tail ledger, dyadic block windows, condensed terms, stream schedules, regular readbacks, dyadic comparison ledger, limit route, Real seal, and structural rows.

The source obligations are finite. Positivity and decreasing behavior are read from $M$ only on the term windows selected by $W$, and the original term observations are read back through $Q$ before any block comparison is formed.

The condensation obligations are carried by $B,G,D$. The dyadic ledger $B$ supplies the finite block endpoints, $G$ forms the corresponding condensed terms, and $D$ records the block inequalities that compare the original tail with the condensed tail on those displayed windows.

The consumer route is then $R$ followed by $E$. The limit-facing row $R$ receives only the partial-sum and condensed-partial-sum windows already displayed, and the Real seal $E$ is reached only after that route has passed through the regular and dyadic ledgers.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since host infinite sums, quotient real equality, countable choice, trichotomy, selected endpoints, and ambient completeness are not coordinates of $K$, they cannot appear as local NameCert obligations.
\end{proof}

\begin{theorem}[CauchyCondensationRealSeries Cauchy route]
\label{thm:cauchy-condensation-real-series-cauchy-route}
Every Real or Completion consumer of an accepted $\CauchyCondensationRealSeriesUp$ packet factors its tail-comparison read through the finite route
$$
A,M\longmapsto B,G\longmapsto W,Q,D\longmapsto R\longmapsto E,H,C,P,N .
$$
Thus the original positive decreasing $\RealSeriesUp$ tail and the condensed tail are compared only by displayed dyadic block windows, scheduled stream reads, regular rational readbacks, and the $\RealSequenceLimitUp$ partial-sum route before any $\RealUp$ seal is visible.
\end{theorem}
\begin{proof}
Start with the accepted carrier. The source row $A$ and monotone ledger $M$ are the only rows from which a consumer can inspect the positive decreasing real-series tail.

Read the dyadic block rows next. The ledger $B$ names the finite block windows, while $G$ names the condensed terms on the same dyadic indices. No consumer can read a condensed comparison without preserving both rows.

Now pass through $W,Q,D$. The schedule $W$ fixes the finite term and partial-sum windows, $Q$ gives the regular rational readback for those windows, and $D$ records the dyadic inequalities that compare each displayed original block with its condensed row.

The partial-sum route $R$ is therefore already a displayed $\RealSequenceLimitUp$ route before the seal $E$ is reached. The remaining rows $H,C,P,N$ preserve and name that same finite route, so the handoff supplies no host infinite sum, quotient real equality, countable-choice schedule, trichotomy split, selected endpoint, or ambient $\RealUp$ completeness theorem.
\end{proof}

\closureat{CauchyCondensationRealSeriesUp}{seedStr}

\begin{closurestatus}{\CauchyCondensationRealSeriesUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-condensation-real-series-carrier}, \autoref{thm:cauchy-condensation-real-series-obligations}, and \autoref{thm:cauchy-condensation-real-series-cauchy-route} seed the finite tail-comparison carrier for positive decreasing $\RealSeriesUp$ terms, dyadic block windows, condensed terms, finite schedules, regular readbacks, dyadic comparison ledgers, limit routing, and Real sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, quotient real equality, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires carrier admission, monotone-tail exposure, dyadic block-window coverage, condensed-term formation, schedule and readback stability, dyadic comparison, limit routing, Real sealing, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCondensationRealSeriesUp.}
  \constructivestory{A $\CauchyCondensationRealSeriesUp$ packet is generated from a positive decreasing RealSeries source row, a monotone-tail ledger, dyadic block windows, condensed terms, StreamName schedules, RegSeqRat readbacks, DyadicRatCore comparison rows, a RealSequenceLimit route, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
