\chapter{A Concrete Naming Certificate for $\OvertRealUp$}
\label{ch:concrete-instances-overt-real-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\OvertRealUp$ packet records positive information about real data as finite witnessable contact, not as a host open-set membership predicate. It sits over the real-name boundary of \autoref{ch:concrete-instances-real-namecert}, the located source interval of \autoref{ch:concrete-instances-located-real-interval-namecert}, the finite interval-cover route of \autoref{ch:concrete-instances-located-interval-cover-namecert}, and the one-sided observation rows of \autoref{ch:concrete-instances-lowerreal-namecert} and \autoref{ch:concrete-instances-upperreal-namecert}. The packet supplies an L10 positive-information interface for downstream real and interval consumers without claiming classical open-cover compactness, arbitrary open-set membership, trichotomy, selected points, or ambient $\RealUp$ completeness.

\begin{definition}[OvertReal carrier]
\label{def:overt-real-carrier}
An $\OvertRealUp$ carrier is a finite $\BHist$ packet
$$
O=(R,I,C,L,U,W,A,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the terminal $\RealUp$ seal row naming the real datum that may be observed only through the displayed real-name route.
\item $I$ is the $\LocatedRealIntervalUp$ source row, exposing endpoint names, radius data, locator reads, locatedness moduli, and metric-bracket rows around the inspected real datum.
\item $C$ is the $\LocatedIntervalCoverUp$ row, recording a finite located cover request through rational intervals, dyadic mesh data, refinement rows, finite windows, and readback data.
\item $L$ is the $\LowerRealUp$ positive lower-observation row. It records finite inhabited lower rational information that may witness nonempty contact from below.
\item $U$ is the $\UpperRealUp$ positive upper-observation row. It records finite upper-bound information that keeps the contact request located rather than host-open.
\item $W$ is the finite witness row naming the particular cover cell, interval bracket, lower read, and upper read used by the positive-information claim.
\item $A$ is the anti-escape ledger saying that the packet exports only witnessable contact and finite cover handoff, not arbitrary open-set membership or open-cover compactness.
\item $H$ records componentwise $\hsame$ transport for $R,I,C,L,U,W,A,P,N$.
\item $T$ records displayed $\Cont$ replay from the real seal to the located interval, from the interval to the cover request, and from the cover request to the lower and upper contact rows.
\item $P$ is the $\Pkg$ provenance over $\OvertRealUp$, $\RealUp$, $\LocatedRealIntervalUp$, $\LocatedIntervalCoverUp$, $\LowerRealUp$, $\UpperRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\OvertRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,I,C,L,U,W,A,H,T,P,N$. It has no coordinate for host open sets, detached membership predicates, arbitrary open covers, compactness extraction, trichotomy, selected representatives, or ambient real completeness.
\end{definition}

\begin{theorem}[OvertReal NameCert obligations]
\label{thm:overt-real-namecert-obligations}
For every accepted $\OvertRealUp$ carrier
$$
O=(R,I,C,L,U,W,A,H,T,P,N),
$$
the local $\NameCert_{\OvertRealUp}$ surface consists exactly of the finite positive-information obligations over the displayed packet:
\begin{enumerate}
\item real-source admission, requiring every real-facing read to pass through the terminal $\RealUp$ row $R$;
\item located-interval admission, requiring endpoint, radius, locator, locatedness, and metric-bracket requests to pass through $I$;
\item finite-cover handoff, requiring every positive contact claim to cite the displayed $\LocatedIntervalCoverUp$ row $C$;
\item one-sided observation exactness, requiring the lower and upper contact reads to be exactly $L$ and $U$;
\item witness-row exactness, requiring the contact witness to be the finite row $W$ and not a selected host point;
\item transport, replay, provenance, and local naming stability through $H,T,P,N$;
\item non-escape through $A$, excluding host open-set membership, arbitrary open-cover compactness, trichotomy, selected representatives, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:overt-real-carrier}. The real datum is visible only through $R$, and the only interval information attached to that datum is the located row $I$.

The positive-information route next passes through $C$. Because $C$ is a $\LocatedIntervalCoverUp$ row, the cover request is finite, located, and routed through displayed rational and dyadic refinement data before any contact claim is available.

The one-sided rows $L$ and $U$ provide the observable lower and upper information. The witness row $W$ binds these reads to one displayed cover cell and interval bracket, so the packet never replaces positive contact by a selected point or by detached host membership.

Finally $H,T,P,N$ transport, replay, source, and name the same rows, while $A$ records the forbidden exits. Since no other coordinate occurs in the carrier, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[OvertReal positive-cover handoff]
\label{thm:overt-real-positive-cover-handoff}
Every $\LocatedIntervalCoverUp$ consumer that asks whether an accepted $\OvertRealUp$ packet has positive contact with a displayed located interval factors through
$$
R,I,C,L,U,W,A,H,T,P,N .
$$
The handoff exposes the source $\RealUp$ seal, the $\LocatedRealIntervalUp$ bracket, the finite $\LocatedIntervalCoverUp$ request, the $\LowerRealUp$ and $\UpperRealUp$ one-sided contact rows, the finite witness row, and the structural transport, replay, provenance, and local naming rows. It exports no host open-set membership predicate, no open-cover compactness theorem, no selected point of contact, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Begin with the accepted carrier $O$. The target consumer is cover-facing, so its first available cover row is the displayed coordinate $C$.

Reading $C$ forces the consumer to retain the source interval row $I$ and the terminal real seal $R$, because the cover route is attached to the located interval around the real datum rather than to an external open-set predicate.

The contact claim is then witnessed by $L,U,W$. The lower and upper rows provide the one-sided positive information, and $W$ records the finite cover cell and bracket in which that information is consumed.

The rows $A,H,T,P,N$ add no extra carrier coordinate. They only block escape, transport the displayed packet, replay the displayed route, record provenance, and name the local certificate. Thus every positive-cover handoff factors through exactly the stated finite surface.
\end{proof}

\closureat{OvertRealUp}{seedStr}

\begin{closurestatus}{\OvertRealUp}
  \constructivestory{An $\OvertRealUp$ packet is generated from a terminal RealUp seal, a LocatedRealIntervalUp source interval, a LocatedIntervalCoverUp finite cover request, LowerRealUp and UpperRealUp one-sided contact rows, a finite witness row, an anti-escape ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:overt-real-carrier}, \autoref{thm:overt-real-namecert-obligations}, and \autoref{thm:overt-real-positive-cover-handoff} seed the finite positive-information surface over $\RealUp$, $\LocatedRealIntervalUp$, $\LocatedIntervalCoverUp$, $\LowerRealUp$, $\UpperRealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim classical open-set membership, arbitrary open-cover compactness, selected points of contact, trichotomy, quotient real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, real-source exactness, located-interval exactness, finite-cover handoff, one-sided contact exactness, witness-row exactness, transport stability, replay stability, and non-escape for BEDC.Derived.OvertRealUp.}
\end{closurestatus}
