\chapter{A Concrete Naming Certificate for $\ClosedPiDomainSubjectReductionUp$}
\label{ch:concrete-instances-closed-pi-domain-subject-reduction-namecert}
\origin{ai}

The $\ClosedPiDomainSubjectReductionUp$ packet realizes the Pi-domain branch of the closed MetaCIC subject-reduction frontier as a finite NameCert carrier. It sits beside the four-row discharge socket of \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}, the discharge ledger of \autoref{ch:concrete-instances-subjectreductiondischargeledger-namecert}, the beta-substitution packet of \autoref{ch:concrete-instances-betasubstitutionpreservation-namecert}, the closed substitution boundary of \autoref{ch:concrete-instances-closed-substitution-boundary-namecert}, and the typed beta congruence trigger of \autoref{ch:concrete-instances-typedbetacongruencetrigger-namecert}. The packet names the Pi-domain obligation as displayed closed term data; it does not export an unconditional closed subject-reduction theorem.

\begin{definition}[ClosedPiDomainSubjectReduction carrier]
\label{def:closed-pi-domain-subject-reduction-carrier}
A $\ClosedPiDomainSubjectReductionUp$ carrier is a finite $\BHist$ packet
$$
P=(T,D,D',C,Y,Z,B,H,R,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the displayed closed Pi term row, naming the source term $\Pi D.\,C$ and its closed context boundary.
\item $D$ is the original domain row, carrying the domain annotation inspected before the congruence step.
\item $D'$ is the reduced domain row reached by the displayed beta step from $D$.
\item $C$ is the codomain row, read under the binder induced by the displayed domain.
\item $Y$ is the typing row, recording the source typing judgement for $\Pi D.\,C$ and the target typing judgement demanded for $\Pi D'.\,C$.
\item $Z$ is the closedness row, requiring the Pi term, original domain, reduced domain, and codomain reads to remain inside the same closed MetaCIC boundary.
\item $B$ is the beta-step and typed congruence row, consuming the displayed Pi-domain beta step and the trigger surface of \autoref{ch:concrete-instances-typedbetacongruencetrigger-namecert}.
\item $H$ records componentwise $\hsame$ transport for $T,D,D',C,Y,Z,B,R,Q,N$.
\item $R$ records displayed $\Cont$ replay from the source Pi term through the domain step, typing row, closedness row, and subject-reduction handoff.
\item $Q$ is the $\Pkg$ provenance over \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}, \autoref{ch:concrete-instances-subjectreductiondischargeledger-namecert}, \autoref{ch:concrete-instances-betasubstitutionpreservation-namecert}, \autoref{ch:concrete-instances-closed-substitution-boundary-namecert}, \autoref{ch:concrete-instances-typedbetacongruencetrigger-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\ClosedPiDomainSubjectReductionUp}$ row.
\end{enumerate}
The classifier accepts only packets displaying the closed Pi term, both domain rows, the codomain row, the typing row, the closedness row, the Pi-domain beta step, transport, replay, provenance, and local naming. It has no coordinate for a blanket closed subject-reduction theorem, a host conversion rule, erased derivation semantics, quotient syntax equality, or an untracked binder context.
\end{definition}

\begin{theorem}[ClosedPiDomainSubjectReduction obligations]
\label{thm:closed-pi-domain-subject-reduction-obligations}
For every accepted $\ClosedPiDomainSubjectReductionUp$ carrier $P=(T,D,D',C,Y,Z,B,H,R,Q,N)$, the local $\NameCert_{\ClosedPiDomainSubjectReductionUp}$ surface consists exactly of carrier admission for the displayed closed Pi term, original domain, reduced domain, codomain, typing row, closedness row, beta-step row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. The Pi-domain preservation read is accepted only when $B$ displays the domain beta step and $Y,Z$ display the corresponding typing and closedness rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:closed-pi-domain-subject-reduction-carrier}. The rows $T,D,D',C$ display the Pi term and the two domain readings, while $Y$ and $Z$ display the typing and closedness boundaries attached to the same context.

The beta-step row $B$ is then read as the Pi-domain congruence trigger. It is not interchangeable with the beta-substitution row, the application-argument row, or the lambda-domain row of the subject-reduction socket, because the target branch changes the displayed Pi domain while preserving the codomain under the induced binder.

The structural rows $H,R,Q,N$ transport, replay, source, and name only that finite packet. Since no row stores a host conversion rule, erased derivation semantics, quotient syntax equality, or a closed subject-reduction theorem, the displayed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[ClosedPiDomainSubjectReduction handoff]
\label{thm:closed-pi-domain-subject-reduction-handoff}
Every subject-reduction discharge ledger read that consumes the Pi-domain branch from an accepted $\ClosedPiDomainSubjectReductionUp$ packet factors through the displayed route
$$
\Pi D.\,C,\ D,\ D',\ C,\ Y,\ Z,\ B,\ H,\ R,\ Q,\ N .
$$
The handoff supplies the Pi-domain obligation row to the subject-reduction discharge socket and ledger; it does not supply the beta-substitution row, application-argument row, lambda-domain row, or an unconditional closed subject-reduction theorem.
\end{theorem}
\begin{proof}
Start with a subject-reduction consumer of the Pi-domain branch. The socket and ledger chapters, \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert} and \autoref{ch:concrete-instances-subjectreductiondischargeledger-namecert}, require a distinct Pi-domain row before the parameterised subject-reduction route can be read.

The present carrier supplies that row only through $T,D,D',C,Y,Z,B$. These rows display the source Pi term, the original and reduced domains, the codomain, the typing judgement, the closedness boundary, and the beta-step trigger.

Finally $H,R,Q,N$ preserve and name the same finite handoff. The beta-substitution preservation packet, closed substitution boundary, and typed beta congruence trigger remain sibling inputs rather than hidden substitute proofs, so the handoff is exactly the Pi-domain row and nothing stronger.
\end{proof}

\falsifiablePrediction{Any accepted $\ClosedPiDomainSubjectReductionUp$ consumer reaching a subject-reduction conclusion without the displayed Pi-domain beta step and typing row refutes the carrier.}

\independenceWitness{metacic-subject-reduction-obligation, betasubstitutionpreservation, closedsubstitutionboundary, typedbetacongruencetrigger: none is bijective with $\ClosedPiDomainSubjectReductionUp$ because this packet jointly carries the closed Pi term, original domain, reduced domain, codomain, typing row, closedness row, Pi-domain beta step, transport, replay, provenance, and local naming.}

The Lean TasteGate file for $\ClosedPiDomainSubjectReductionUp$ must provide explicit $\mathsf{Nontrivial}\ \ClosedPiDomainSubjectReductionUp$ and $\mathsf{FieldFaithful}\ \ClosedPiDomainSubjectReductionUp$ instances preserving $T,D,D',C,Y,Z,B,H,R,Q,N$ as distinct rows.

\closureat{ClosedPiDomainSubjectReductionUp}{seedStr}

\begin{closurestatus}{\ClosedPiDomainSubjectReductionUp}
  \constructivestory{A $\ClosedPiDomainSubjectReductionUp$ packet is generated from a closed Pi term row, original domain row, reduced domain row, codomain row, typing row, closedness row, beta-step row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:closed-pi-domain-subject-reduction-carrier}, \autoref{thm:closed-pi-domain-subject-reduction-obligations}, and \autoref{thm:closed-pi-domain-subject-reduction-handoff} seed the finite Pi-domain subject-reduction obligation packet for the closed MetaCIC discharge route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close beta-substitution preservation, application-argument stability, lambda-domain preservation, unconditional closed subject reduction, host conversion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Pi-domain beta-step exactness, typing-row exposure, closedness-row exposure, subject-reduction ledger handoff, and TasteGate field faithfulness for BEDC.Derived.ClosedPiDomainSubjectReductionUp.}
\end{closurestatus}
