\chapter{A Concrete Naming Certificate for $\FiniteTraceInductionGapUp$}
\label{ch:concrete-instances-finite-trace-induction-gap-namecert}
\origin{human}

Following the Bishop and Brouwer distinction between finite verification and an induction schema, the $\FiniteTraceInductionGapUp$ packet records the finite-observation side of \autoref{def:transcendental-input-finite-trace} and the non-internal-induction boundary of \autoref{thm:transcendental-input-no-internal-induction}. It sits beside the finite-trace GAP socket of \autoref{ch:concrete-instances-finite-trace-gap-socket-namecert}, the transcendental induction socket of \autoref{ch:concrete-instances-transcendentalinductionsocket-namecert}, and the closed-observation ledger of \autoref{ch:concrete-instances-closedobservationsystem-namecert}. The packet names a finite verification trace together with the GAP socket exposed by any attempted universal closure; it does not install a substrate-internal universal quantifier, dependent induction schema, host recursor, or future-observation oracle.

\begin{definition}[Finite trace induction gap carrier]
\label{def:finite-trace-induction-gap-carrier}
A $\FiniteTraceInductionGapUp$ carrier is a finite $\BHist$ packet
$$
G=(T,O,A,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the finite verification trace row, listing only the observed indices and their closed-generation witness records.
\item $O$ is the observed predicate row, storing the finite family of predicate reads actually checked by the trace.
\item $A$ is the attempted induction-closure row, naming the requested passage from the finite trace to a universal claim without admitting the passage as a carrier coordinate.
\item $Q$ is the GAP socket row exposed when $A$ asks for substrate-internal induction beyond the displayed trace.
\item $H$ records componentwise $\hsame$ transport for the finite trace, observed predicate rows, attempted closure row, GAP socket, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each observed predicate read through $T,O,A,Q,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteTraceInductionGapUp$, $\FiniteTraceGapSocketUp$, $\TranscendentalInductionSocketUp$, $\ClosedObservationSystemUp$, $\BHist$, $\Gap$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteTraceInductionGapUp}$ row.
\end{enumerate}
The classifier accepts only packets whose finite trace, observed predicate rows, attempted induction-closure row, GAP socket, transport, replay, provenance, and local naming are all displayed. It has no coordinate for a universal quantifier over unobserved indices, a substrate-internal induction schema, a host dependent recursor, an infinite observation ledger, or a future-observation oracle.
\end{definition}

\begin{theorem}[Finite trace induction gap NameCert obligations]
\label{thm:finite-trace-induction-gap-namecert-obligations}
For every accepted $\FiniteTraceInductionGapUp$ carrier $G=(T,O,A,Q,H,C,P,N)$, the local $\NameCert_{\FiniteTraceInductionGapUp}$ surface consists exactly of carrier admission for the finite trace row, observed predicate rows, attempted induction-closure row, GAP socket row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Any consumer that asks for induction closure must expose $A$ and then consume $Q$ as a GAP socket; no substrate-internal universal statement is exported by the packet.
\end{theorem}
\begin{proof}
Project the accepted carrier. The projection exposes the finite trace $T$, the observed predicate rows $O$, the attempted closure row $A$, the GAP socket $Q$, and the structural rows $H,C,P,N$.

Read the induction request through $A$. If the consumer stays within the finite trace, it can use only the displayed rows $T$ and $O$. If it asks for all unobserved indices, the next displayed row is the GAP socket $Q$, not a universal witness.

The transport and replay rows preserve that boundary. Since no universal quantifier, dependent induction schema, host recursor, infinite ledger, or future-observation oracle is a coordinate of $G$, the local NameCert obligations are exhausted by the finite trace and GAP route.
\end{proof}

\begin{theorem}[Finite trace induction gap non-escape]
\label{thm:finite-trace-induction-gap-nonescape}
Every induction-facing consumer of an accepted $\FiniteTraceInductionGapUp$ packet factors through
$$
T \longmapsto O \longmapsto A \longmapsto Q \longmapsto H,C,P,N .
$$
Thus the consumer may read the observed finite trace and the displayed predicate witnesses, but any attempted export of a universal induction claim reaches only the GAP socket. The packet exports no substrate-internal universal quantifier, no closed dependent recursor, no infinite observation object, and no promise over future observations.
\end{theorem}
\begin{proof}
Start with the carrier rows of \autoref{def:finite-trace-induction-gap-carrier}. The trace row $T$ and observed predicate row $O$ give exactly the finite witness records already present in the closed observational system.

The attempted closure row $A$ names the requested induction passage. It is deliberately followed by the GAP socket row $Q$, so a consumer that asks for unobserved indices receives a visible boundary rather than a hidden induction rule.

Finally replay and transport the same route through $C$ and $H$, then read provenance and local naming through $P,N$. The excluded universal, recursor, infinite-ledger, and future-observation objects are absent from the carrier, so the displayed GAP route is exhaustive.
\end{proof}

\closureat{FiniteTraceInductionGapUp}{seedStr}

\begin{closurestatus}{\FiniteTraceInductionGapUp}
  \constructivestory{A $\FiniteTraceInductionGapUp$ packet is generated from a finite verification trace, observed predicate rows, an attempted induction-closure row, a GAP socket, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-trace-induction-gap-carrier}, \autoref{thm:finite-trace-induction-gap-namecert-obligations}, and \autoref{thm:finite-trace-induction-gap-nonescape} seed the finite verification trace and induction-GAP boundary for closed observational systems.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a substrate-internal universal quantifier, dependent induction schema, host recursor, infinite observation ledger, future-observation oracle, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-trace visibility, observed-predicate stability, induction-GAP routing, non-escape, transport, replay, provenance, and local naming for BEDC.Derived.FiniteTraceInductionGapUp.}
\end{closurestatus}
