\chapter{A Concrete Naming Certificate for $\FiniteRealCoverUp$}
\label{ch:concrete-instances-finite-real-cover-namecert}
\origin{human}

Following Bishop and Bridges and Kelley, the $\FiniteRealCoverUp$ packet records the finite ball-cover data used by metric and compact-metric arguments without importing arbitrary open-cover compactness or a choice-selected subcover. It sits over the $\MetricUp$ surface of \autoref{ch:concrete-instances-metric-namecert}, the $\RealUp$ distance seal of \autoref{ch:concrete-instances-real-namecert}, the dyadic radius arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the total-bounded witness interface of \autoref{ch:concrete-instances-totallybounded-namecert}, and the compact-metric consumer route of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet names only finite ball rows, dyadic radii, coverage witnesses, refinement ledgers, componentwise transport, replay, provenance, and local naming evidence.

\begin{definition}[Finite real cover carrier]
\label{def:finite-real-cover-carrier}
A $\FiniteRealCoverUp$ carrier is a finite $\BHist$ packet
$$
F=(M,R,D,B,W,E,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $M$ is the accepted $\MetricUp$ row whose distance observations are sealed through $\RealUp$;
\item $R$ is a finite row of $\RealUp$ or metric source probes to be covered;
\item $D$ is the $\DyadicRatCoreUp$ radius ledger, with each radius recorded as a positive dyadic tolerance;
\item $B$ is the finite ball row assigning each listed center and dyadic radius to its displayed metric-distance witness;
\item $W$ is the coverage witness row, pairing each inspected source probe in $R$ with an admitted ball in $B$ and its distance bound;
\item $E$ is the refinement ledger, recording how a finer finite ball row reuses or refines the displayed centers, dyadic radii, and coverage witnesses;
\item $H$ is the componentwise $\hsame$ transport row for the metric, probe, radius, ball, coverage, refinement, provenance, and local naming coordinates;
\item $C$ is the displayed $\Cont$ replay route for metric distance reads, radius reads, coverage reads, and refinement reads;
\item $P$ is the $\Pkg$ provenance over $\MetricUp$, $\RealUp$, $\DyadicRatCoreUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\FiniteRealCoverUp}$ evidence.
\end{enumerate}
The carrier has no coordinate for an arbitrary open cover, a host finite-subcover selection function, a powerset compactness theorem, a quotient real equality, or an ambient completeness object.
\end{definition}

\begin{definition}[Finite real cover classifier]
\label{def:finite-real-cover-classifier}
Two accepted $\FiniteRealCoverUp$ packets
$$
F=(M,R,D,B,W,E,H,C,P,N)
$$
and
$$
F'=(M',R',D',B',W',E',H',C',P',N')
$$
are classified together exactly when the stored $\hsame$ rows transport $M$ to $M'$, $R$ to $R'$, $D$ to $D'$, $B$ to $B'$, $W$ to $W'$, $E$ to $E'$, $P$ to $P'$, and $N$ to $N'$, and the displayed $\Cont$ rows replay the same metric-distance, dyadic-radius, coverage, and refinement route on both packets. The classifier does not compare host subsets, arbitrary cover families, selected subcovers, completed metric spaces, or quotient real representatives.
\end{definition}

\begin{theorem}[Finite real cover NameCert obligations]
\label{thm:finite-real-cover-namecert-obligations}
For the carrier of \autoref{def:finite-real-cover-carrier}, the local $\NameCert_{\FiniteRealCoverUp}$ surface consists exactly of carrier admission for $F=(M,R,D,B,W,E,H,C,P,N)$, classifier stability by \autoref{def:finite-real-cover-classifier}, metric-distance witness admission through $M$, dyadic radius admission through $D$, finite ball admission through $B$, coverage witness admission through $W$, refinement-ledger admission through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier. Its rows display the metric source, inspected probes, dyadic radii, ball witnesses, coverage witnesses, refinement ledger, transport, replay, provenance, and local name as one finite packet.

Use the classifier definition for stability. It compares only the displayed rows and transports them componentwise through $\hsame$, then replays the same route through $C$.

The omitted open-cover, subcover-choice, quotient, and completeness objects are not coordinates of $F$. Coordinate exhaustion therefore leaves exactly the listed NameCert obligations.
\end{proof}

\begin{theorem}[Finite real cover refinement stability]
\label{thm:finite-real-cover-refinement-stability}
Any accepted refinement read of a $\FiniteRealCoverUp$ packet must pass through the displayed refinement ledger $E$. If a finer packet refines $F$, the read transports the metric row $M$, dyadic radius ledger $D$, ball row $B$, and coverage row $W$ through the stored $\hsame$ entries and replays the same $\Cont$ route before the finer coverage witnesses are exposed. It cannot replace the ledger by a host cover refinement, arbitrary finite-subcover choice, completed metric compactness result, or quotient real equality.
\end{theorem}
\begin{proof}
Start with a refinement-facing consumer. Carrier projection gives access only to the rows $M,R,D,B,W,E,H,C,P,N$.

The refinement ledger $E$ is the only row whose role is to relate the displayed balls, dyadic radii, and coverage witnesses to a finer finite ball row. Transport through $H$ preserves those coordinates componentwise, and replay through $C$ preserves the metric and dyadic reads.

Since no host refinement operation or subcover selector is stored in the packet, the accepted refinement remains the finite ledger route described above.
\end{proof}

\begin{theorem}[Finite real cover total-bounded handoff]
\label{thm:finite-real-cover-total-bounded-handoff}
Every $\TotallyBoundedUp$ or $\CompactMetricUp$ consumer citing an accepted $\FiniteRealCoverUp$ packet receives a finite handoff through
$$
M \longmapsto D \longmapsto B \longmapsto W \longmapsto E.
$$
The handoff supplies the metric-distance witness, dyadic tolerance, finite ball row, coverage witness, and refinement ledger needed by total-bounded and compact-metric reads. It supplies no general open-cover compactness theorem, no choice-selected subcover, no ambient powerset cover object, no independent complete-metric carrier, and no quotient real representative.
\end{theorem}
\begin{proof}
Read the consumer through the carrier. The metric row $M$ gives the distance source, $D$ gives the dyadic tolerance budget, $B$ gives the finite ball witnesses, and $W$ gives the coverage witnesses.

For refinement-sensitive consumers, apply refinement stability. The ledger $E$ keeps finer covers inside the same finite ball and dyadic-radius route before any total-bounded or compact-metric handoff is exported.

The listed excluded objects are not stored in the carrier, classifier, transport, replay, provenance, or local NameCert rows. Therefore the total-bounded and compact-metric handoff is exhausted by the displayed finite route.
\end{proof}

\begin{closurestatus}{\FiniteRealCoverUp}
  \constructivestory{A $\FiniteRealCoverUp$ packet is generated from a metric source row, Real-valued distance probes, dyadic radius rows, finite ball rows, coverage witnesses, a refinement ledger, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite carrier, classifier, NameCert obligations, refinement stability, and total-bounded handoff for explicit metric ball covers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close arbitrary open-cover compactness, choice-selected subcovers, hyperspace compactness, quotient real equality, or ambient metric completion.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, coverage-witness nonescape, refinement-ledger stability, and total-bounded handoff for BEDC.Derived.FiniteRealCoverUp.}
\end{closurestatus}
