\chapter{A Concrete Naming Certificate for $\AbsolutelyContinuousFunctionUp$}
\label{ch:concrete-instances-absolute-continuous-function-namecert}
\origin{human}

Following Bishop and Bridges and the constructive bounded-variation treatment, the $\AbsolutelyContinuousFunctionUp$ packet records absolute continuity on a displayed real interval as finite partition control, variation budget, derivative/integral ledger, and real-name handoff data rather than as a host function quotient or a measure-completed derivative theorem. It sits after the regulated-function carrier of \autoref{ch:concrete-instances-regulated-function-namecert}, the bounded-variation ledger of \autoref{ch:concrete-instances-boundedvariation-namecert}, the integral surface of \autoref{ch:concrete-instances-integral-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives Real and Completion consumers a finite route for interval variation requests before any ambient measure algebra, selected derivative, host function equality, or completed $L^1$ object is available.

\begin{definition}[AbsoluteContinuousFunction carrier]
\label{def:absolute-continuous-function-carrier}
An $\AbsolutelyContinuousFunctionUp$ carrier is a finite $\BHist$ packet
$$
A=(I,F,M,P,V,D,L,T,W,Q,R,H,C,S,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the source interval row, exposing the endpoint real-name windows, orientation data, and compact subinterval request on which the function is inspected.
\item $F$ is the displayed real-valued function row, read only through finite input windows and output $\RealUp$ seals.
\item $M$ is the modulus row assigning, for each dyadic error budget, a finite interval-length budget used by the absolute-continuity test.
\item $P$ is the finite disjoint-partition ledger. It lists the inspected interval family, total displayed length, endpoint windows, and the corresponding value-jump windows.
\item $V$ is the $\BoundedVariationUp$ budget row asserting that the finite sum of visible jumps along $P$ is controlled by the error budget selected by $M$.
\item $D$ is the derivative ledger row. It records only displayed derivative-window requests and their local variation accounting.
\item $L$ is the $\IntegralUp$ handoff row for the interval derivative or variation-density request consumed by integration-facing clients.
\item $T$ is the $\RegulatedFunctionUp$ approximation row used to expose stepwise endpoint behavior before the gauge row is read.
\item $W$ is the $\StreamNameUp$ finite-window row selecting the interval, partition, derivative, integral, regulated approximation, and seal observations consumed by the packet.
\item $Q$ is the $\RegSeqRatUp$ readback row for interval lengths, output jumps, regulated approximants, and integral estimates.
\item $R$ is the terminal $\RealUp$ seal row reached by downstream Real and Completion consumers after the partition, regulated, gauge, regular, and dyadic rows have been displayed.
\item $H$ stores componentwise $\hsame$ transport for interval, function, modulus, partition, variation, derivative, integral, regulated, stream, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from an absolute-continuity request through the same finite rows.
\item $S$ is the $\Pkg$ provenance over $\AbsolutelyContinuousFunctionUp$, $\RegulatedFunctionUp$, $\BoundedVariationUp$, $\IntegralUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AbsolutelyContinuousFunctionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for host function equality, quotient real functions, measure completion, a selected derivative, countable additivity, ambient variation space completion, or a completed $L^1$ representative.
\end{definition}
\leanchecked{BEDC.Derived.AbsolutelyContinuousFunctionUp.AbsolutelyContinuousFunctionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[AbsoluteContinuousFunction NameCert obligations]
\label{thm:absolute-continuous-function-namecert-obligations}
For every accepted $\AbsolutelyContinuousFunctionUp$ carrier $A=(I,F,M,P,V,D,L,T,W,Q,R,H,C,S,N)$, the local $\NameCert_{\AbsolutelyContinuousFunctionUp}$ surface consists exactly of carrier admission; partition-refinement stability through $P$ and $W$; variation-budget exactness through $V$; derivative/integral ledger handoff through $D,L$; regulated approximation through $T$; StreamName and RegSeqRat readback through $W,Q$; Real seal nonescape through $R$; componentwise transport, displayed replay, provenance, and local naming through $H,C,S,N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:absolute-continuous-function-carrier}. The visible rows are exactly $I,F,M,P,V,D,L,T,W,Q,R,H,C,S,N$, so every local naming obligation must be read from one of those rows.

The source and control obligations are $I,F,M,P,V$. The interval and function rows determine the inspected endpoint windows, while the modulus row chooses the finite length budget. The partition and variation ledgers then record the only admissible test that small total displayed length forces small total displayed jump.

The analytic handoff obligations are $D,L,T,W,Q,R$. The derivative ledger records the local window request, the integral row carries the integration-facing handoff, the regulated row exposes stepwise endpoint behavior, and the stream and regular rows provide the finite numerical readbacks before the terminal Real seal is visible.

Finally $H,C,S,N$ transport, replay, source, and name the same packet. Since no carrier coordinate stores host function equality, quotient real functions, measure completion, a selected derivative, countable additivity, ambient variation space completion, or a completed $L^1$ representative, none of those objects can appear in the local NameCert surface.
\end{proof}

\begin{theorem}[AbsoluteContinuousFunction bounded-variation handoff]
\label{thm:absolute-continuous-function-bounded-variation-handoff}
Every bounded-variation or fundamental-theorem consumer reads an accepted $\AbsolutelyContinuousFunctionUp$ packet only through the displayed $\RegulatedFunctionUp$, $\BoundedVariationUp$, $\IntegralUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route
$$
I,F,M\longmapsto P,V\longmapsto D,L,T\longmapsto W,Q\longmapsto R,H,C,S,N .
$$
Thus a consumer reaches the $\IntegralUp$ row only after the absolute-continuity partition budget and $\BoundedVariationUp$ ledger have been displayed, and reaches the $\RealUp$ seal only after regulated approximation, StreamName windows, and regular rational readback have also been displayed.
\end{theorem}
\begin{proof}
Start with the interval, function, and modulus rows. They fix the displayed real interval, the finite function windows, and the dyadic budget used by the absolute-continuity request.

The partition route is next. The row $P$ lists the inspected disjoint intervals and their total displayed length, and $V$ records the corresponding finite jump bound. No gauge-facing read is available before these rows have been consumed.

Only then does the route reach the derivative, integral, and regulated rows. The derivative ledger $D$ records the local request, the $\IntegralUp$ row $L$ receives the integration-facing handoff, and the $\RegulatedFunctionUp$ row $T$ supplies the stepwise approximation boundary.

The sibling dependency is exact: the bounded-variation row is read through \autoref{ch:concrete-instances-boundedvariation-namecert}, the regulated approximation through \autoref{ch:concrete-instances-regulated-function-namecert}, the integral handoff through \autoref{ch:concrete-instances-integral-namecert}, and the terminal numerical route through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

The terminal read is numerical and sealed. Rows $W$ and $Q$ provide finite observation windows and regular rational comparisons for the displayed estimates, while $R,H,C,S,N$ seal, transport, replay, source, and name the packet. Hence the exported handoff is finite BEDC route data, not a host derivative theorem, measure-completed integral, quotient function equality, or selected $L^1$ representative.
\end{proof}

\begin{theorem}[AbsoluteContinuousFunction partition-modulus stability]
\label{thm:absolute-continuous-function-partition-modulus-stability}
Let $A=(I,F,M,P,V,D,L,T,W,Q,R,H,C,S,N)$ and $A'=(I',F',M,P',V',D',L',T',W',Q',R',H',C',S',N')$ be accepted $\AbsolutelyContinuousFunctionUp$ packets sharing the same modulus row $M$. If their partition ledgers $P$ and $P'$ are related componentwise by $\hsame$ through the transport row $H$, then the variation-budget row $V$ exports the same absolute-continuity jump bound before any derivative row, integral handoff, or Real seal is read.
\end{theorem}
\begin{proof}
Project the two accepted carriers through \autoref{def:absolute-continuous-function-carrier}. The shared row $M$ fixes the dyadic length budget used by both absolute-continuity requests, while $P$ and $P'$ list the corresponding displayed disjoint interval families.

Use the componentwise $\hsame$ data in $H$ to compare the partition ledgers. Since the comparison is rowwise over the displayed endpoint windows and total-length entries, the same partition budget is presented to the variation row on both sides.

Now read the variation-budget obligation from \autoref{thm:absolute-continuous-function-namecert-obligations}. The row $V$ is upstream of $D,L,T,W,Q,R$, so the equality of jump bounds is obtained before derivative requests, integral handoffs, regulated approximations, numerical readbacks, or Real seals can contribute extra data.
\end{proof}

\begin{theorem}[AbsoluteContinuousFunction Real and Completion consumer boundary]
\label{thm:absolute-continuous-function-real-completion-consumer-boundary}
Every Real or Completion consumer of an accepted $\AbsolutelyContinuousFunctionUp$ packet factors through the displayed rows
$$
M \longmapsto P \longmapsto V \longmapsto T \longmapsto W \longmapsto Q \longmapsto R
$$
in that order before it exports an endpoint, variation, or integral-facing real read. Such a consumer cannot replace the route by host function equality, quotient real functions, measure completion, selected derivatives, countable additivity, or ambient $L^1$ completion.
\end{theorem}
\begin{proof}
Begin with the control rows. The modulus row $M$ chooses the finite length budget, the partition ledger $P$ displays the inspected intervals, and the variation row $V$ records the corresponding finite jump bound.

Next compose with the bounded-variation handoff of \autoref{thm:absolute-continuous-function-bounded-variation-handoff}. It places the regulated approximation row $T$ before the StreamName and RegSeqRat reads, so a Real or Completion consumer must pass through the displayed approximation boundary before any terminal numerical seal is available.

Finally read $W,Q,R$. The finite observation windows, regular rational comparisons, and Real seal are the only consumer-facing numerical route, and the carrier has no coordinate for host function equality, quotient real functions, measure completion, selected derivatives, countable additivity, or ambient $L^1$ completion.
\end{proof}

\closureat{AbsolutelyContinuousFunctionUp}{seedStr}

\begin{closurestatus}{\AbsolutelyContinuousFunctionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:absolute-continuous-function-carrier}, \autoref{thm:absolute-continuous-function-namecert-obligations}, and \autoref{thm:absolute-continuous-function-bounded-variation-handoff} seed the finite absolute-continuity route over interval, function, modulus, partition, bounded-variation, derivative, integral, regulated, StreamName, regular, Real seal, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host function equality, quotient real functions, measure completion, selected derivatives, countable additivity, ambient variation space completion, completed $L^1$ representatives, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, partition coverage, variation-budget exactness, derivative and integral handoff, regulated approximation, StreamName windows, RegSeqRat readback, Real sealing, transport, replay, provenance, and local naming for BEDC.Derived.AbsoluteContinuousFunctionUp.}
  \constructivestory{An $\AbsolutelyContinuousFunctionUp$ packet is generated from an interval row, displayed real-valued function row, modulus budget, disjoint-partition ledger, bounded-variation budget, derivative ledger, Integral handoff, RegulatedFunction approximation, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
