\chapter{A Concrete Naming Certificate for $\BornologyUp$}
\label{ch:concrete-instances-bornology-namecert}
\origin{human}

Following Bourbaki and Kelley on bornologies, the $\BornologyUp$ packet records the finite bounded-family interface that sits between the bounded-subset certificate of \autoref{ch:concrete-instances-boundedset-namecert}, the directed base surface of \autoref{ch:concrete-instances-filterbase-namecert}, the uniform entourage surface of \autoref{ch:concrete-instances-uniformspace-namecert}, and the Cauchy-family specialization of \autoref{ch:concrete-instances-cauchy-bornology-namecert}. It names bounded families by displayed hereditary and finite-union rows before any completion, uniform, or Real-facing consumer can ask for a selected bound, a quotient family, countable choice, host suprema, or ambient completeness.

\begin{definition}[Bornology carrier]
\label{def:bornology-carrier}
A $\BornologyUp$ carrier is a finite $\BHist$ packet
$$
B=(F,S,U,E,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the bounded-family source row. It lists the finite family requests that may be read as bounded data.
\item $S$ is the subset-heredity ledger, recording that an accepted subfamily request is read only through a displayed parent family already named by $F$.
\item $U$ is the finite-union ledger, recording binary and finite union requests as displayed rows over previously accepted bounded families.
\item $E$ is the singleton and source-exposure row, naming the basic bounded packets available before hereditary or union closure is inspected.
\item $D$ is the consumer handoff row for $\FilterBaseUp$ or $\UniformSpaceUp$ readers, and for the $\CauchyBornologyUp$ specialization of the same bounded-family surface.
\item $H$ records componentwise $\hsame$ transport for $F,S,U,E,D,C,P,N$.
\item $C$ records displayed $\Cont$ replay from bounded-family admission through subset heredity, finite union, source exposure, consumer handoff, transport, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\BornologyUp$, $\BoundedSetUp$, $\FilterBaseUp$, $\UniformSpaceUp$, $\CauchyBornologyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BornologyUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through these rows. It has no coordinate for host suprema, selected bounds, quotient families, countable choice, open-cover compactness, or ambient completeness.
\end{definition}

\begin{theorem}[Bornology NameCert obligations]
\label{thm:bornology-namecert-obligations}
For every accepted $\BornologyUp$ carrier $B=(F,S,U,E,D,H,C,P,N)$, the local $\NameCert_{\BornologyUp}$ surface consists exactly of carrier admission, bounded-family source exposure, subset-heredity ledger visibility, finite-union ledger visibility, singleton and source exposure, $\FilterBaseUp$ or $\UniformSpaceUp$ consumer handoff, $\CauchyBornologyUp$ specialization handoff, componentwise transport, displayed continuation replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Carrier admission projects the displayed packet. The source row $F$ and singleton/source row $E$ expose the basic bounded-family entries before any closure rule is read.

Subset heredity is confined to $S$, and finite union is confined to $U$. These ledgers are rows of the same packet, so a consumer cannot replace them by a host powerset, a selected bound, or a quotient family.

The handoff row $D$ then presents the same bounded-family surface to $\FilterBaseUp$, $\UniformSpaceUp$, and $\CauchyBornologyUp$ consumers. The structural rows $H,C,P,N$ transport, replay, source, and name only the displayed packet.
\end{proof}

\begin{theorem}[Bornology bounded-family union stability]
\label{thm:bornology-bounded-family-union-stability}
Let $B=(F,S,U,E,D,H,C,P,N)$ be an accepted $\BornologyUp$ carrier. Every accepted finite union of displayed bounded-family reads is certified by the finite-union ledger $U$ after the source row $F$ and singleton/source row $E$ have been exposed, and every accepted subfamily of such a union is routed back through the subset-heredity ledger $S$. The route exports no host supremum, selected bound, quotient family, countable-choice selector, open-cover compactness principle, or ambient completeness premise.
\end{theorem}
\begin{proof}
Read the carrier rows. Source and singleton exposure are the only entry points for basic bounded-family data, so a union request must first cite displayed rows from $F$ and $E$.

The finite-union ledger $U$ records the admitted union row. A later subfamily request cannot inspect that union through a host family predicate; it must pass through $S$, whose parent row is already displayed inside the packet.

Transport and replay through $H$ and $C$ preserve the same ledgers, while $P$ and $N$ package only the named dependencies and local certificate. Therefore the union-stability route remains finite and contains none of the excluded host principles.
\end{proof}

\begin{theorem}[Bornology CauchyBornology handoff]
\label{thm:bornology-cauchy-bornology-handoff}
Every $\CauchyBornologyUp$ consumer of an accepted $\BornologyUp$ carrier reads the general bounded-family surface through
$$
F,E \longmapsto S,U \longmapsto D \longmapsto H,C,P,N .
$$
Thus the Cauchy specialization receives bounded-family source rows, singleton exposure, subset heredity, finite-union stability, consumer handoff, transport, replay, provenance, and local naming before it may open rate budgets, regular rational readback, Real seals, or completion-facing data.
\end{theorem}
\begin{proof}
Start with a $\CauchyBornologyUp$ consumer. The only general bornology data available to it are the displayed source and singleton rows $F,E$.

The closure properties are read next. Subset heredity is supplied by $S$, and finite union is supplied by $U$, so the consumer receives the ordinary bornological closure rows before any Cauchy-specific budget or Real-facing row can be inspected.

The handoff is then the row $D$, preserved by $H$ and replayed by $C$. Since $P$ and $N$ name only the general bounded-family packet and its Cauchy specialization, the route adds no selected bound, quotient family, countable-choice selector, host supremum, or ambient completeness premise.
\end{proof}

\closureat{BornologyUp}{seedStr}

\begin{closurestatus}{\BornologyUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bornology-carrier}, \autoref{thm:bornology-namecert-obligations}, \autoref{thm:bornology-bounded-family-union-stability}, and \autoref{thm:bornology-cauchy-bornology-handoff} seed the finite bounded-family NameCert surface over bounded-set, filter-base, uniform-space, and Cauchy-bornology consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host suprema, selected bounds, quotient families, countable choice, open-cover compactness, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure asks for checked carrier admission, bounded-family source exposure, subset-heredity stability, finite-union stability, singleton/source exposure, consumer handoff, transport, replay, provenance, and local naming for BEDC.Derived.BornologyUp.}
  \constructivestory{A $\BornologyUp$ packet is generated from bounded-family source rows, subset-heredity ledgers, finite-union ledgers, singleton and source exposure, FilterBaseUp or UniformSpaceUp handoff rows, CauchyBornologyUp specialization, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
