\chapter{A Concrete Naming Certificate for $\RealArchimedeanPropertyUp$}
\label{ch:concrete-instances-real-archimedean-property-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealArchimedeanPropertyUp$ packet records the finite BEDC surface by which a displayed $\RealUp$ name receives a natural-number bound and the corresponding rational and dyadic comparison rows. It sits next to the $\RealArchimedeanBoundSchemaUp$ neighbour of \autoref{ch:concrete-instances-real-archimedean-bound-schema-namecert}, but it names the property-level handoff: every bound read starts from the $\RealUp$ name of \autoref{ch:concrete-instances-real-namecert}, passes through $\NatUp$ of \autoref{ch:concrete-instances-nat-namecert}, $\RatUp$ of \autoref{ch:concrete-instances-rat-namecert}, $\DyadicRatCoreUp$ of \autoref{ch:concrete-instances-dyadicratcore-namecert}, $\StreamNameUp$ of \autoref{ch:concrete-instances-streamname-namecert}, and $\RegSeqRatUp$ of \autoref{ch:concrete-instances-regseqrat-namecert}, and only then exposes an Archimedean bound ledger. The packet is a finite naming certificate for that route, not a host real-order axiom, trichotomy principle, quotient-real equality, or completeness theorem.

\begin{definition}[RealArchimedeanProperty carrier]
\label{def:real-archimedean-property-carrier}
A $\RealArchimedeanPropertyUp$ carrier is a finite $\BHist$ packet
$$
A=(R,n,q,d,S,G,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ name whose finite real observations are being bounded.
\item $n$ is the $\NatUp$ bound row, recording the natural-number index used by the bound.
\item $q$ is the $\RatUp$ comparison row naming the rational face of the same bound.
\item $d$ is the $\DyadicRatCoreUp$ comparison row naming the dyadic face of the same bound.
\item $S$ is the $\StreamNameUp$ finite-window row inspected before the comparison is read.
\item $G$ is the $\RegSeqRatUp$ readback row that turns the inspected stream window into a regular rational Cauchy observation.
\item $B$ is the Archimedean bound ledger, compatible with the $\RealArchimedeanBoundSchemaUp$ route of \autoref{ch:concrete-instances-real-archimedean-bound-schema-namecert}.
\item $H$ records componentwise $\hsame$ transport for the real name, natural bound, rational row, dyadic row, stream window, readback row, bound ledger, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a bound request through $S$, $G$, $q$, $d$, and $n$.
\item $P$ is the $\Pkg$ provenance over $\RealArchimedeanPropertyUp$, $\RealUp$, $\NatUp$, $\RatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealArchimedeanBoundSchemaUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealArchimedeanPropertyUp}$ row.
\end{enumerate}
The carrier accepts only packets whose real observation, bound index, rational and dyadic comparisons, stream inspection, regular rational readback, bound ledger, transport, replay, provenance, and local name are all displayed in the same finite certificate.
\end{definition}

\begin{theorem}[RealArchimedeanProperty NameCert obligations]
\label{thm:real-archimedean-property-namecert-obligations}
For every accepted $\RealArchimedeanPropertyUp$ carrier $A=(R,n,q,d,S,G,B,H,C,P,N)$, the local $\NameCert_{\RealArchimedeanPropertyUp}$ surface consists exactly of carrier admission for the displayed $\RealUp$ name, $\NatUp$ bound row, $\RatUp$ comparison row, $\DyadicRatCoreUp$ comparison row, $\StreamNameUp$ finite-window row, $\RegSeqRatUp$ readback row, Archimedean bound ledger, componentwise transport through $H$, displayed continuation replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$. No obligation may read a host real-order axiom, trichotomy oracle, quotient-real equality, selected unbounded search, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier. The rows $R,n,q,d,S,G,B,H,C,P,N$ are the only coordinates available to the local certificate, so carrier admission and local naming are finite ledger facts.

The observation route begins with $R$ and the inspected stream window $S$. The readback row $G$ turns that finite window into the rational Cauchy surface already accepted by $\RegSeqRatUp$.

The bound route then reads $q$, $d$, and $n$ as the rational, dyadic, and natural faces of the same displayed bound ledger $B$. The transport and replay rows preserve exactly these coordinates, and the provenance row names the sibling chapters from which they are read.

Since the carrier has no coordinate for host order, trichotomy, quotient equality, an unbounded search principle, or completeness, none of those principles can enter the local $\NameCert$ obligations.
\end{proof}

\begin{theorem}[RealArchimedeanProperty natural-rational bound handoff]
\label{thm:real-archimedean-property-nat-rat-bound-handoff}
Every order-facing or approximation-facing consumer of an accepted $\RealArchimedeanPropertyUp$ packet reaches the natural bound row only through the finite route
$$
\RealUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RatUp,\ \DyadicRatCoreUp \longmapsto \NatUp.
$$
The rational and dyadic comparison rows are read before the natural-number bound is exported, and the same handoff is compatible with the $\RealArchimedeanBoundSchemaUp$ ledger of \autoref{ch:concrete-instances-real-archimedean-bound-schema-namecert}.
\end{theorem}
\begin{proof}
Begin with a consumer requesting a bound for the displayed real name. The continuation row $C$ first routes the request through the finite $\StreamNameUp$ window $S$ and the $\RegSeqRatUp$ readback row $G$.

The comparison rows $q$ and $d$ are then read as rational and dyadic witnesses for the same inspected real observation. Only after these rows are displayed does the natural-number row $n$ become available as the bound face of the ledger $B$.

The compatibility with $\RealArchimedeanBoundSchemaUp$ is structural: both packets expose the same real, stream, regular readback, rational, dyadic, and bound-ledger coordinates. The property packet adds the explicit $\NatUp$ handoff without adding host order or completeness data.
\end{proof}

\begin{theorem}[RealArchimedeanProperty ledger nonescape]
\label{thm:real-archimedean-property-ledger-nonescape}
For an accepted $\RealArchimedeanPropertyUp$ packet, every Archimedean-property read factors through the displayed rows $R,n,q,d,S,G,B,H,C,P,N$. In particular, the packet exports no hidden real supremum, no total order trichotomy, no quotient equality of real names, no unbounded search over naturals, no selected least bound, and no completeness principle for $\RealUp$.
\end{theorem}
\begin{proof}
Inspect the carrier inventory. The only real-facing row is $R$, the only finite observation rows are $S$ and $G$, the only comparison rows are $q$ and $d$, and the only natural bound row is $n$.

The replay row $C$ can only traverse those displayed coordinates, while $H$ transports them componentwise and $P,N$ package the same route as provenance and local naming. Thus any Archimedean-property read must pass through the finite ledger described in the carrier.

Because no row stores a supremum, trichotomy decision, quotient equality test, unbounded natural search, selected least-bound operator, or completeness theorem, the packet cannot export any of those structures.
\end{proof}

\closureat{RealArchimedeanPropertyUp}{seedStr}

\begin{closurestatus}{\RealArchimedeanPropertyUp}
  \constructivestory{A $\RealArchimedeanPropertyUp$ packet is generated from a RealUp name, NatUp bound row, RatUp comparison row, DyadicRatCoreUp comparison row, StreamNameUp finite-window row, RegSeqRatUp readback row, Archimedean bound ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-archimedean-property-carrier}, \autoref{thm:real-archimedean-property-namecert-obligations}, \autoref{thm:real-archimedean-property-nat-rat-bound-handoff}, and \autoref{thm:real-archimedean-property-ledger-nonescape} seed the finite property-level bound route over Real, StreamName, RegSeqRat, Rat, DyadicRatCore, Nat, and RealArchimedeanBoundSchema rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real order, trichotomy, quotient equality of real names, unbounded search, least-bound selection, Real completeness, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, natural-rational-dyadic bound compatibility, finite-window readback, transport stability, replay stability, and ledger nonescape for BEDC.Derived.RealArchimedeanPropertyUp.}
\end{closurestatus}
