\chapter{A Concrete Naming Certificate for $\RealBolzanoUp$}
\label{ch:concrete-instances-real-bolzano-namecert}
\origin{human}

Following Bolzano and Bishop--Bridges constructive analysis, the $\RealBolzanoUp$ packet records sign-change bracketing as finite Real-and-Completion route data. It sits over the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the interval comparison surfaces of \autoref{ch:concrete-instances-closedboundedinterval-namecert}, \autoref{ch:concrete-instances-regular-cauchy-comparison-namecert}, and \autoref{ch:concrete-instances-real-root-bracket-namecert}. The packet supplies a displayed bracket for later intermediate-value and root-isolation consumers without importing real trichotomy, unrestricted intermediate value, quotient real equality, selected roots, or ambient $\RealUp$ completeness.

\begin{definition}[RealBolzano carrier]
\label{def:real-bolzano-carrier}
A $\RealBolzanoUp$ carrier is a finite $\BHist$ packet
$$
B=(a,b,L,U,S,D,J,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $a$ and $b$ are endpoint real-name rows, each read through the $\RealUp$ seal route and exposed only as finite regular windows.
\item $L$ and $U$ are the left and right located sign witnesses, recording displayed apartness-from-zero evidence at the inspected endpoint windows.
\item $S$ is the sign-change ledger, requiring the two endpoint sign witnesses to be opposed at the requested dyadic precision.
\item $D$ is the dyadic bracket ledger, storing the interval endpoints, midpoint requests, tolerance radii, and width comparisons used by the finite bisection route.
\item $J$ is the comparison row, carrying the ordered interval and nonescape checks that keep every retained bracket inside the displayed endpoint interval.
\item $R$ is the $\RegSeqRatUp$ handoff row assembled from the retained bracket windows and dyadic tolerance ledger.
\item $E$ is the terminal $\RealUp$ seal boundary reached only after the endpoint rows, located sign witnesses, bracket ledger, comparison row, and regular handoff have been displayed.
\item $H$ records componentwise $\hsame$ transport for the endpoint, sign, bracket, comparison, regular handoff, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite sign-change request through $a,b,L,U,S,D,J,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RealBolzanoUp$, $\RealUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, the closed bounded interval route, the regular Cauchy comparison route, $\RealRootBracketUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealBolzanoUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $a,b,L,U,S,D,J,R,E,H,C,P,N$. It has no coordinate for real trichotomy, unrestricted intermediate value, a selected zero, quotient real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RealBolzano NameCert obligations]
\label{thm:real-bolzano-namecert-obligations}
For every accepted $\RealBolzanoUp$ carrier
$$
B=(a,b,L,U,S,D,J,R,E,H,C,P,N),
$$
the local $\NameCert_{\RealBolzanoUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for endpoint real rows, located sign witnesses, dyadic bracket ledger, comparison row, regular handoff, real seal boundary, transport, replay, provenance, and local naming;
\item endpoint sign exposure, requiring $L$ and $U$ to be read after the endpoint real-name rows $a,b$ and to expose only located apartness data at displayed precision;
\item bracket-refinement stability, requiring each retained interval in $D$ to preserve the displayed sign-change ledger $S$ and to decrease the bracket width by dyadic comparison;
\item comparison nonescape, requiring $J$ to keep every retained bracket inside the original displayed closed bounded interval;
\item $\RegSeqRatUp$ handoff routing, requiring $R$ to be assembled from the retained bracket windows and dyadic tolerance ledger rather than from a selected root;
\item $\RealUp$ seal routing, requiring $E$ to remain downstream of $a,b,L,U,S,D,J,R$;
\item componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$ for the same rows;
\item refusal of real trichotomy, unrestricted intermediate value, selected roots, quotient real equality, and ambient $\RealUp$ completeness as certificate data.
\end{enumerate}
No RealBolzano obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-bolzano-carrier}. The endpoint rows $a,b$ are the only real-name sources, and the located sign rows $L,U$ expose sign information only at displayed precision.

The bracket route is finite. The ledger $S$ records the sign-change request, while $D$ stores the dyadic interval, midpoint, tolerance, and width-comparison data used by each retained bracket. The comparison row $J$ keeps each retained interval inside the original closed bounded interval.

The completion-facing rows are downstream of that bracket route. The row $R$ assembles the regular rational handoff from the retained bracket windows, and the seal $E$ is read only after $a,b,L,U,S,D,J,R$ have been displayed.

Finally $H,C,P,N$ transport, replay, source, and name the same packet rows. Since no excluded order, selection, quotient, or completeness coordinate occurs in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{Every accepted $\RealBolzanoUp$ read factors through two endpoint Real rows, two located sign witnesses, one sign-change ledger, one dyadic bracket ledger, one comparison row, one RegSeqRat handoff, one terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming before any intermediate-value or root-bracketing consumer may inspect it.}

\independenceWitness{real, regseqrat, dyadicratcore, closedboundedinterval, regular-cauchy-comparison, real-root-bracket: $\RealBolzanoUp$ is not bijective to any listed sibling because it jointly carries endpoint real rows, located sign witnesses, a sign-change ledger, dyadic bracket refinement, comparison nonescape, regular handoff, real seal routing, transport, replay, provenance, and local naming.}

\closureat{RealBolzanoUp}{seedStr}

\begin{closurestatus}{\RealBolzanoUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-bolzano-carrier} and \autoref{thm:real-bolzano-namecert-obligations} seed the constructive sign-change bracketing packet over endpoint Real rows, located sign witnesses, dyadic bracket ledgers, comparison nonescape, RegSeqRat handoff, Real seal routing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim real trichotomy, unrestricted intermediate value, selected roots, quotient real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint sign exposure, bracket-refinement stability, comparison nonescape, RegSeqRat handoff routing, Real seal routing, transport, replay, provenance, and local naming for BEDC.Derived.RealBolzanoUp.}
  \constructivestory{A $\RealBolzanoUp$ packet is generated from endpoint Real rows, located sign witnesses, a sign-change ledger, dyadic bracket refinement, comparison rows, a RegSeqRat handoff, a terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
