\chapter{A Concrete Naming Certificate for $\CauchyCompletionReflectionUp$}
\label{ch:concrete-instances-cauchy-completion-reflection-namecert}
\origin{human}

Following Bishop and Bridges constructive completion and Kelley reflection terminology, the $\CauchyCompletionReflectionUp$ packet records the finite BEDC boundary where Cauchy completion data reflect through the displayed unit and counit routes before reaching the Real seal. It reads the dense unit route of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the completed-object return route of \autoref{ch:concrete-instances-cauchy-completion-counit-namecert}, the comparison surface of \autoref{ch:concrete-instances-cauchy-completion-comparison-namecert}, the broader completion-reflection boundary of \autoref{ch:concrete-instances-completionreflection-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a nonquotient reflection certificate for displayed completion routes; it does not identify quotient completions, choose stream representatives, assert host equality, invoke countable choice, or import ambient completeness of $\RealUp$.

\begin{definition}[CauchyCompletionReflection carrier]
\label{def:cauchy-completion-reflection-carrier}
A $\CauchyCompletionReflectionUp$ carrier is a finite $\BHist$ packet
$$
R=(U,V,Q,F,S,D,A,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\CauchyCompletionUnitUp$ row admitting source data into the completion-facing presentation.
\item $V$ is the $\CauchyCompletionCounitUp$ row returning completed data to a displayed completion consumer.
\item $Q$ is the $\CauchyCompletionComparisonUp$ row comparing the unit/universal-property presentation with the functorial metric-completion presentation.
\item $F$ is the $\CompletionReflectionUp$ row tying the unit and counit routes to the same reflection boundary.
\item $S$ is the finite $\StreamNameUp$ window family inspected before any terminal seal can be read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the stream windows.
\item $A$ is the $\RegSeqRatUp$ regular rational readback row shared by the unit, counit, comparison, and reflection routes.
\item $E$ is the terminal $\RealUp$ seal row reached only after $S,D,A$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $U,V,Q,F,S,D,A,E$ and the structural rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
U,V,Q,F \longmapsto S,D,A \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionReflectionUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionCounitUp$, $\CauchyCompletionComparisonUp$, $\CompletionReflectionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionReflectionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected representatives, host equality of completed objects, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[CauchyCompletionReflection NameCert obligations]
\label{thm:cauchy-completion-reflection-namecert-obligations}
For every accepted $\CauchyCompletionReflectionUp$ carrier
$$
R=(U,V,Q,F,S,D,A,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionReflectionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the unit route, counit route, comparison row, reflection row, stream windows, dyadic ledger, regular readback, Real seal, transport, replay, provenance, and local naming row;
\item unit exposure, requiring source admission to pass through $U$ before a completion-facing read can inspect $Q$ or $F$;
\item counit exposure, requiring completed-object return to pass through $V$ before the same $Q,F$ reflection boundary is read;
\item comparison agreement, requiring the unit route and counit route to use the shared $\CauchyCompletionComparisonUp$ row $Q$ before the finite analytic route is public;
\item reflection stability, requiring $F$ to be the only reflection witness tying $U,V,Q$ to the terminal seal;
\item finite seal routing, requiring all Real-facing reads to pass through $S,D,A,E$ and then through $H,C,P,N$;
\item non-escape, requiring the packet to source and name no quotient completion equality, selected representative, host equality, countable-choice schedule, open-cover compactness, or ambient $\RealUp$ completeness theorem.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-reflection-carrier}. The accepted tuple exposes exactly the unit, counit, comparison, reflection, analytic readback, and structural rows listed there.

For the unit side, the source row is read through $U$ before any completion-facing comparison is available. For the counit side, the completed-object return is read through $V$ before the same comparison and reflection boundary can be inspected.

The comparison and reflection obligations use $Q$ and $F$. The comparison row identifies the displayed completion presentations, while $F$ records that both the unit and counit reads are attached to the same completion-reflection boundary.

Finally the finite seal route is forced through $S,D,A,E$. Induction on the finite $\StreamNameUp$ windows in $S$ shows that each inspected window carries only its dyadic tolerance row and regular rational readback before the terminal $\RealUp$ seal is reached. The transport, replay, provenance, and naming rows $H,C,P,N$ preserve only these displayed coordinates, so no excluded completion or choice principle is exported.
\end{proof}

\begin{theorem}[CauchyCompletionReflection unit-counit triangle]
\label{thm:cauchy-completion-reflection-unit-counit-triangle}
Let
$$
R=(U,V,Q,F,S,D,A,E,H,C,P,N)
$$
be an accepted $\CauchyCompletionReflectionUp$ carrier. Every consumer that compares the unit route with the counit route factors through the finite triangle
$$
U,V \longmapsto Q,F \longmapsto S,D,A \longmapsto E .
$$
The triangle is a displayed NameCert route over $\CauchyCompletionUnitUp$, $\CauchyCompletionCounitUp$, $\CauchyCompletionComparisonUp$, $\CompletionReflectionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. It is not quotient completion equality, not selected representative equality, not host equality of completed objects, not countable choice, and not ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Project the accepted carrier. A unit-facing read has access to $U$, and a counit-facing read has access to $V$; neither route contains a terminal seal on its own.

The two reads meet only at $Q$ and $F$. The comparison row supplies the shared completion presentation, and the reflection row records the boundary that both the unit and counit routes must use.

The remaining analytic data are $S,D,A,E$. Induction on the finite stream-window family shows that every triangle consumer sees exactly the window row, attached dyadic tolerance, regular rational readback, and Real seal before the structural rows $H,C,P,N$ replay and name the route. Since no other coordinate is present, the excluded quotient, representative, host-equality, choice, and completeness data cannot be read.
\end{proof}

\begin{theorem}[CauchyCompletionReflection Real-seal handoff]
\label{thm:cauchy-completion-reflection-real-seal-handoff}
For an accepted $\CauchyCompletionReflectionUp$ carrier $R=(U,V,Q,F,S,D,A,E,H,C,P,N)$, every Real-facing completion-reflection consumer receives the terminal seal $E$ only through the route
$$
U,V,Q,F \longmapsto S,D,A \longmapsto E \longmapsto H,C,P,N .
$$
Thus the handoff to $\RealUp$ is mediated by the sibling $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ rows and by the displayed $\CompletionReflectionUp$ boundary. It exports no quotient completion equality, selected representative, host equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness theorem, Lean bridge, or detached seal.
\end{theorem}
\begin{proof}
Start with a Real-facing consumer. Projection of the accepted carrier gives the only available completion-reflection rows: $U,V,Q,F$ and the finite analytic route $S,D,A,E$.

The consumer cannot read $E$ before the sibling route has been displayed. The stream windows in $S$ determine the finite observations, $D$ supplies their tolerances, and $A$ supplies the regular rational readback.

After $E$ is reached, $H$ and $C$ transport and replay the same route, while $P$ and $N$ source and name it. No carrier coordinate stores a quotient completion, selected representative, host equality, choice schedule, compactness argument, ambient real-completeness theorem, Lean bridge, or detached seal, so no Real-facing handoff can export one.
\end{proof}

\closureat{CauchyCompletionReflectionUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionReflectionUp}
  \constructivestory{A $\CauchyCompletionReflectionUp$ packet is generated from CauchyCompletionUnit and CauchyCompletionCounit routes, a CauchyCompletionComparison row, a CompletionReflection witness, finite StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a terminal Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-reflection-carrier}, \autoref{thm:cauchy-completion-reflection-namecert-obligations}, \autoref{thm:cauchy-completion-reflection-unit-counit-triangle}, and \autoref{thm:cauchy-completion-reflection-real-seal-handoff} seed the finite nonquotient reflection boundary for L10 completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host equality, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, unit exposure, counit exposure, comparison agreement, reflection stability, finite seal routing, non-escape, and a Lean carrier/obligation formalization for BEDC.Derived.CauchyCompletionReflectionUp.}
\end{closurestatus}
