\chapter{A Concrete Naming Certificate for $\RieszLemmaUp$}
\label{ch:concrete-instances-riesz-lemma-namecert}
\origin{human}

Following Riesz's lemma in normed linear spaces, the $\RieszLemmaUp$ packet records the finite BEDC witness by which a proper closed subspace and a displayed separation tolerance expose a normed-space separation row. It sits over the norm carrier of \autoref{ch:concrete-instances-norm-namecert}, the inner-product comparison surface of \autoref{ch:concrete-instances-innerproduct-namecert}, the metric observation row of \autoref{ch:concrete-instances-metric-namecert}, the complete-metric boundary of \autoref{ch:concrete-instances-completemetric-namecert}, and the Banach carrier of \autoref{ch:concrete-instances-banach-namecert}. The certificate names a finite separation witness surface; it is not a quotient subspace construction, not a selected best approximation, and not an ambient compactness or completeness theorem.

\begin{definition}[Riesz lemma finite separation carrier]
\label{def:riesz-lemma-carrier}
A $\RieszLemmaUp$ carrier is a finite $\BHist$ packet
$$
R=(X,Y,U,A,B,D,S,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the normed-space source row, read through $\NormUp$ and the vector-space carrier already visible to the packet.
\item $Y$ is the displayed proper closed subspace row, named as finite membership and closure evidence rather than as a quotient carrier.
\item $U$ is the unit normalization row recording the inspected vector window and its norm-one certificate.
\item $A$ is the separation tolerance row, with the requested dyadic margin read through the local $\DyadicRatCoreUp$ ledger.
\item $B$ is the ball-avoidance row recording the displayed finite comparisons with the subspace window.
\item $D$ is the metric-distance observation row, routed through $\MetricUp$ and the norm-induced distance surface.
\item $S$ is the separation witness row that names the finite vector witness after $U,A,B,D$ have been read.
\item $K$ is the completeness or Banach-facing source row, available only as a dependency witness from $\CompleteMetricUp$ or $\BanachUp$ and not as a selection principle.
\item $H$ stores componentwise $\hsame$ transports for the displayed rows.
\item $C$ stores the displayed $\Cont$ replay route from source and subspace rows to the witness row.
\item $P$ is the $\Pkg$ provenance over the normed source, subspace ledger, tolerance, avoidance, distance, witness, transport, replay, and local naming rows.
\item $N$ is the local $\NameCert_{\RieszLemmaUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these finite rows. It has no coordinate for quotient subspace distance, best-approximation selection, closed-ball compactness, countable choice, or ambient Banach-space completeness.
\end{definition}
\leanchecked{BEDC.Derived.RieszLemmaUp.RieszLemmaTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Riesz lemma NameCert obligations]
\label{thm:riesz-lemma-namecert-obligations}
For every accepted $\RieszLemmaUp$ carrier $R=(X,Y,U,A,B,D,S,K,H,C,P,N)$, the local NameCert surface consists of:
\begin{enumerate}
\item carrier admission for the finite normed-separation packet of \autoref{def:riesz-lemma-carrier};
\item source-row exposure through $X$, with the norm and metric rows read through \autoref{ch:concrete-instances-norm-namecert} and \autoref{ch:concrete-instances-metric-namecert};
\item subspace exposure through $Y$, with closure information displayed as finite ledger data rather than quotient subspace distance;
\item unit and tolerance exposure through $U$ and $A$ before any avoidance or separation row is visible;
\item classifier stability through $B,D,S$, where ball avoidance, metric observation, and separation witness rows are compared componentwise;
\item ledger nonescape through $K,H,C,P,N$, so completeness, transport, replay, provenance, and naming remain inside the same finite packet.
\end{enumerate}
These obligations do not include a quotient normed space, a nearest-point projection, a selected distance minimizer, countable choice, compactness of closed balls, or an unrestricted Banach-space separation principle.
\end{theorem}
\begin{proof}
Project the carrier rows of \autoref{def:riesz-lemma-carrier}. The source, subspace, unit, tolerance, avoidance, distance, witness, completeness-source, transport, replay, provenance, and naming rows are the only data visible to the local classifier.

The normed-separation part is finite. The source row $X$ supplies the normed carrier, $Y$ supplies the displayed subspace ledger, and $U,A$ fix the unit normalization and dyadic tolerance before any witness can be read.

The classifier stability part is read through $B,D,S$. These rows compare avoidance and distance observations componentwise, so the separation witness cannot be replaced by quotient distance or by a selected best approximation.

Finally $K,H,C,P,N$ bind the route to one local certificate. Since the excluded objects are absent from the carrier, no NameCert obligation can escape through them.
\end{proof}
\leanchecked{BEDC.Derived.RieszLemmaUp.RieszLemmaCarrier\_namecert\_obligations}

\begin{theorem}[Riesz lemma normed separation witness]
\label{thm:riesz-lemma-normed-separation-witness}
Every consumer of an accepted $\RieszLemmaUp$ packet that asks for the Riesz separation witness factors through
$$
X,Y,U,A,B,D,S,K,H,C,P,N .
$$
The read consumes the normed source, closed-subspace ledger, unit normalization, tolerance row, ball-avoidance row, metric-distance observation, separation witness row, completeness-source row, componentwise transport, replay, provenance, and local naming before any witness is exported. The route exports no quotient subspace distance, selected minimizer, host projection, compactness principle, countable choice, or ambient Banach-space completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:riesz-lemma-namecert-obligations}. They place $X,Y,U,A$ before the avoidance and distance rows, so the requested separation witness is grounded in displayed normed-space and subspace data.

Next read $B,D,S$. The avoidance row, metric observation row, and separation witness row are compared by the local classifier, which makes the witness stable under componentwise equality of the displayed packet.

Finally use the ledger rows $K,H,C,P,N$. They record that completeness dependencies, transport, continuation replay, provenance, and local naming stay inside the same finite $\BHist$ packet. Hence the consumer receives a finite normed separation witness rather than any of the excluded quotient, choice, projection, compactness, or ambient-completeness objects.
\end{proof}

\closureat{RieszLemmaUp}{seedStr}

\begin{closurestatus}{\RieszLemmaUp}
  \constructivestory{A $\RieszLemmaUp$ packet is generated from a normed-space source row, closed-subspace ledger, unit normalization row, dyadic tolerance, ball-avoidance row, metric-distance observation, separation witness, completeness-source dependency, componentwise transport, continuation replay, package provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riesz-lemma-carrier}, \autoref{thm:riesz-lemma-namecert-obligations}, and \autoref{thm:riesz-lemma-normed-separation-witness} bind the finite normed-space separation carrier and its witness nonescape boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{The chapter does not claim quotient subspace distance, nearest-point projection, selected distance minimizers, compactness of closed balls, countable choice, full Banach-space separation, bridge checking, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability for the avoidance and distance rows, ledger nonescape, and local NameCert coverage for the displayed normed separation packet.}
\end{closurestatus}
