\chapter{A Concrete Naming Certificate for $\RealCauchyDenseEmbeddingUp$}
\label{ch:concrete-instances-real-cauchy-dense-embedding-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy real names, the $\RealCauchyDenseEmbeddingUp$ packet records the finite route by which a regular Cauchy rational name is admitted into the $\RealUp$ seal. It sits after the regular-rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the dense-embedding route of \autoref{ch:concrete-instances-regular-cauchy-dense-embedding-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet exposes the source-to-seal admission route without importing quotient real equality, selected representatives, trichotomy, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[RealCauchyDenseEmbedding carrier]
\label{def:real-cauchy-dense-embedding-carrier}
A $\RealCauchyDenseEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
E=(R,W,D,J,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RegSeqRatUp$ source row, exposing the regular Cauchy rational name and its displayed modulus discipline;
\item $W$ is the $\StreamNameUp$ window row used to inspect the finite source entries requested by a real-name consumer;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the requested precision, comparison budget, and slack rows used by the admission route;
\item $J$ is the $\RegularCauchyDenseEmbeddingUp$ route row that names the dense source-to-real embedding discipline;
\item $S$ is the terminal $\RealUp$ seal row reached only after $R,W,D,J$ have been displayed;
\item $H$ records componentwise $\hsame$ transport for the regular source, windows, dyadic ledger, dense-embedding route, Real seal, replay, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ replay from a Real-admission request through $R,W,D,J,S,H$;
\item $P$ is the $\Pkg$ provenance over $\RealCauchyDenseEmbeddingUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyDenseEmbeddingUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RealCauchyDenseEmbeddingUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for quotient real equality, a selected representative of a real name, countable choice over approximation stages, trichotomy, a host completion operator, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RealCauchyDenseEmbedding NameCert obligations]
\label{thm:real-cauchy-dense-embedding-namecert-obligations}
For every accepted $\RealCauchyDenseEmbeddingUp$ carrier $E=(R,W,D,J,S,H,C,P,N)$, the local $\NameCert_{\RealCauchyDenseEmbeddingUp}$ surface consists exactly of carrier admission for the regular-rational source $R$, finite window exposure through $W$, dyadic tolerance accounting through $D$, dense-embedding routing through $J$, Real-seal handoff through $S$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$. A $\RealUp$ or completion-facing consumer must read $R,W,D,J$ before the seal row $S$ is available.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-cauchy-dense-embedding-carrier}. The regular source, finite windows, dyadic tolerance ledger, dense-embedding route, Real seal, transport, replay, provenance, and local naming rows are exactly the displayed coordinates.

The source side is finite. The $\RegSeqRatUp$ row supplies the regular Cauchy rational name, the $\StreamNameUp$ row opens only the requested windows, and the $\DyadicRatCoreUp$ row records the tolerance ledger used by those windows.

The dense-embedding row $J$ then mediates admission to the Real seal. The row $S$ is downstream of $R,W,D,J$, and the structural rows $H,C,P,N$ preserve and name the same route, so the certificate surface cannot expose quotient real equality, selected representatives, trichotomy, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[RealCauchyDenseEmbedding Real-seal nonescape]
\label{thm:real-cauchy-dense-embedding-real-seal-nonescape}
Every $\RealUp$-facing consumer of an accepted $\RealCauchyDenseEmbeddingUp$ packet receives the finite route
$$
\RegSeqRatUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegularCauchyDenseEmbeddingUp \longmapsto \RealUp \longmapsto \hsame,\Cont,\Pkg,\NameCert .
$$
The terminal $\RealUp$ row is only a seal for the displayed regular Cauchy rational source and its finite tolerance windows. It is not a source of quotient real equality, selected representatives, countable choice, trichotomy, host completion, or ambient real completeness.
\end{theorem}
\begin{proof}
Start with the obligation surface of \autoref{thm:real-cauchy-dense-embedding-namecert-obligations}. A consumer cannot read the Real seal until the regular source, finite windows, dyadic tolerance ledger, and dense-embedding route have already been displayed.

The sibling rows enforce the direction of the read. $\RegSeqRatUp$ supplies the source name, $\StreamNameUp$ supplies only finite windows, $\DyadicRatCoreUp$ supplies the precision ledger, and $\RegularCauchyDenseEmbeddingUp$ supplies the source-to-seal route.

Finally the rows $H,C,P,N$ transport, replay, source, and name the same packet. Since no refused host-side principle is a coordinate of $E$, the Real row remains a seal and not an escape principle.
\end{proof}

\falsifiablePrediction{Every accepted $\RealCauchyDenseEmbeddingUp$ consumer reads one $\RegSeqRatUp$ source row, one $\StreamNameUp$ finite-window row, one $\DyadicRatCoreUp$ tolerance ledger, and one $\RegularCauchyDenseEmbeddingUp$ route before any $\RealUp$ seal is exposed.}

\independenceWitness{regseqrat, streamname, dyadicratcore, regular-cauchy-dense-embedding, real: $\RealCauchyDenseEmbeddingUp$ is not bijective to any listed sibling because it jointly carries source regularity, finite windows, dyadic tolerance accounting, dense-embedding routing, Real seal handoff, transport, replay, provenance, and local naming.}

\closureat{RealCauchyDenseEmbeddingUp}{seedStr}

\begin{closurestatus}{\RealCauchyDenseEmbeddingUp}
  \constructivestory{A $\RealCauchyDenseEmbeddingUp$ packet is generated from a RegSeqRat source row, finite StreamName windows, a DyadicRatCore tolerance ledger, a RegularCauchyDenseEmbedding route, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-cauchy-dense-embedding-carrier}, \autoref{thm:real-cauchy-dense-embedding-namecert-obligations}, and \autoref{thm:real-cauchy-dense-embedding-real-seal-nonescape} seed the finite regular-Cauchy rational source-to-Real seal admission packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient real equality, selected representatives, countable choice, trichotomy, host completion, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source regularity, finite window exposure, dyadic tolerance accounting, dense-embedding routing, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.RealCauchyDenseEmbeddingUp.}
\end{closurestatus}
