\chapter{A Concrete Naming Certificate for $\DnaWindowSixBoundaryTileUp$}
\label{ch:concrete-instances-dna-window-six-boundary-tile-namecert}
\origin{ai}

The $\DnaWindowSixBoundaryTileUp$ packet realizes the finite stop/Trp and Ile/Met $X_2\sqcup\{11\}$ boundary-tile surface of \autoref{thm:philosophy-stop-trp-boundary-tile} and \autoref{thm:philosophy-ile-met-boundary-tile} as BEDC NameCert data. It consumes the six-coordinate codon source window of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the standard-code transition rows of \autoref{ch:concrete-instances-codon-transition-matrix-namecert}, the stop-suffix packet of \autoref{ch:concrete-instances-stopcodonzeckendorfsuffix-namecert}, and the spectral stabilization route of \autoref{ch:concrete-instances-spectral-stabilization-namecert}. The packet records the two boundary tiles as finite classifier rows, not as a hidden biological table or an ambient stochastic model.

\begin{definition}[DnaWindowSixBoundaryTile carrier]
\label{def:dna-window-six-boundary-tile-carrier}
A $\DnaWindowSixBoundaryTileUp$ carrier is a finite $\BHist$ packet
$$
T=(W,M,B,I,S,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ source-window row exposing the six bit coordinates of the relevant codon windows;
\item $M$ is the $\CodonTransitionMatrixUp$ row exposing the standard-code bridge rows used to read stop, tryptophan, isoleucine, methionine, and initiation contexts;
\item $B$ is the finite boundary-tile classifier row, recording the stop/Trp tile $\mathrm{U}+\mathrm{RR}+X_2/11$ and the Ile/Met tile $\mathrm{AU}+X_2/11$;
\item $I$ is the Ile/Met initiation handoff row, distinguishing the Met amino-acid row from the canonical start bridge row when initiation context is present;
\item $S$ is the $\StopCodonZeckendorfSuffixUp$ stop-suffix handoff row for the stop-side tile;
\item $L$ is the $\SpectralStabilizationUp$ sibling route row used by finite consumers that compare the same stop-face boundary with spectral support data;
\item $H$ records componentwise $\hsame$ transport for source windows, transition rows, boundary tiles, initiation handoff, stop suffix, spectral route, replay, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ replay from a boundary-tile request through $W,M,B,I,S,L,H$;
\item $P$ is the $\Pkg$ provenance over $\DnaWindowSixBoundaryTileUp$, $\CodonSixBitWindowUp$, $\CodonTransitionMatrixUp$, $\StopCodonZeckendorfSuffixUp$, $\SpectralStabilizationUp$, the source vision of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\DnaWindowSixBoundaryTileUp}$ row.
\end{enumerate}
The classifier accepts only packets whose stop/Trp and Ile/Met boundary reads are exhausted by $W,M,B,I,S,L,H,C,P,N$. It has no coordinate for a hidden codon table, global biological semantics, probabilistic inference, quotient codon equality, or a selected stochastic process.
\end{definition}

\begin{theorem}[DnaWindowSixBoundaryTile NameCert obligations]
\label{thm:dna-window-six-boundary-tile-namecert-obligations}
For every accepted $\DnaWindowSixBoundaryTileUp$ carrier $T=(W,M,B,I,S,L,H,C,P,N)$, the local $\NameCert_{\DnaWindowSixBoundaryTileUp}$ surface consists exactly of source-window admission through $W$, standard-code bridge-row admission through $M$, boundary-tile classifier exactness through $B$, initiation handoff through $I$, stop-suffix handoff through $S$, spectral-stabilization sibling routing through $L$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:dna-window-six-boundary-tile-carrier}. The source window, transition bridge, boundary classifier, initiation handoff, stop suffix, spectral sibling route, transport, replay, provenance, and local naming rows are the only displayed coordinates.

The stop/Trp tile and the Ile/Met tile are finite classifier reads. The row $W$ supplies the six coordinate positions, $M$ supplies the standard-code bridge rows, and $B$ records the two $X_2\sqcup\{11\}$ partitions.

The rows $I,S,L$ keep the initiation, stop-suffix, and spectral consumers attached to the same boundary-tile surface. Finally $H,C,P,N$ transport, replay, source, and name that surface, so no hidden codon table, global biological semantics, probabilistic inference, quotient codon equality, or selected stochastic process is exported.
\end{proof}

\begin{theorem}[DnaWindowSixBoundaryTile consumer nonescape]
\label{thm:dna-window-six-boundary-tile-consumer-nonescape}
Every accepted consumer of a $\DnaWindowSixBoundaryTileUp$ packet reads the route
$$
\CodonSixBitWindowUp,\ \CodonTransitionMatrixUp \longmapsto B,I,S,L \longmapsto \hsame,\Cont,\Pkg,\NameCert .
$$
Thus the six-coordinate codon window and standard-code bridge rows are read before any stop/Trp, Ile/Met, initiation, stop-suffix, or spectral-stabilization consumer can use the boundary-tile classifier. The route exports no hidden biological table, global semantics, probabilistic inference, quotient codon equality, or selected stochastic model.
\end{theorem}
\begin{proof}
Use \autoref{thm:dna-window-six-boundary-tile-namecert-obligations}. The boundary classifier row $B$ is downstream of the source-window row $W$ and standard-code bridge row $M$.

The initiation, stop-suffix, and spectral rows are also downstream. They may consume the displayed boundary-tile classifier, but they do not replace the six-coordinate source window or the standard-code bridge rows.

The structural rows $H,C,P,N$ preserve and name the same finite route. Since the carrier contains no row for the refused external principles, every accepted consumer remains inside the displayed packet.
\end{proof}

\falsifiablePrediction{Any accepted $\DnaWindowSixBoundaryTileUp$ consumer omitting the six-coordinate $\CodonSixBitWindowUp$ source window or the standard-code $\CodonTransitionMatrixUp$ bridge rows refutes the packet.}

\independenceWitness{codon-six-bit-window, codon-transition-matrix, stopcodonzeckendorfsuffix, spectral-stabilization: $\DnaWindowSixBoundaryTileUp$ is not bijective to any listed sibling because it jointly carries two boundary-tile classifier rows, initiation handoff, stop-suffix routing, spectral sibling routing, transport, replay, provenance, and local naming.}

The Lean TasteGate route for \texttt{BEDC.Derived.DnaWindowSixBoundaryTileUp} must provide explicit $\Nontrivial\ \DnaWindowSixBoundaryTileUp$ and $\FieldFaithful\ \DnaWindowSixBoundaryTileUp$ instances preserving $W,M,B,I,S,L,H,C,P,N$ as separate displayed fields.

\closureat{DnaWindowSixBoundaryTileUp}{seedStr}

\begin{closurestatus}{\DnaWindowSixBoundaryTileUp}
  \constructivestory{A $\DnaWindowSixBoundaryTileUp$ packet is generated from codon six-bit windows, standard-code bridge rows, finite stop/Trp and Ile/Met boundary-tile classifiers, initiation handoff, stop-suffix handoff, spectral sibling routing, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dna-window-six-boundary-tile-carrier}, \autoref{thm:dna-window-six-boundary-tile-namecert-obligations}, and \autoref{thm:dna-window-six-boundary-tile-consumer-nonescape} seed the finite boundary-tile packet over codon windows and standard-code bridge rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological table identity, global biological semantics, probabilistic inference, quotient codon equality, selected stochastic modeling, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, boundary-tile classifier exactness, initiation handoff, stop-suffix handoff, spectral sibling routing, transport, replay, provenance, local naming, Nontrivial DnaWindowSixBoundaryTileUp, and FieldFaithful DnaWindowSixBoundaryTileUp for BEDC.Derived.DnaWindowSixBoundaryTileUp.}
\end{closurestatus}
