\chapter{A Concrete Naming Certificate for $\FilterConvergenceUp$}
\label{ch:concrete-instances-filter-convergence-namecert}
\origin{human}

Following Kelley and Bourbaki on filter convergence, the $\FilterConvergenceUp$ packet records the finite convergence interface needed by the L10 completion route. It sits between the finite $\CauchyFilterUp$ surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the regular directed-tail surface of \autoref{ch:concrete-instances-regularcauchyfilter-namecert}, the window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the ambient metric interface of \autoref{ch:concrete-instances-metric-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names convergence toward a displayed target point through visible tail events and tolerance rows; it does not quotient filters, select host limits, invoke countable choice, hide cofinal tails, or assume ambient real completeness.

\begin{definition}[FilterConvergence carrier]
\label{def:filter-convergence-carrier}
A $\FilterConvergenceUp$ carrier is a finite $\BHist$ packet
$$
F=(B,X,T,V,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the visible $\CauchyFilterUp$ row. It stores the finite filterbase requests and refinement evidence from which convergence may be read.
\item $X$ is the target point row over $\MetricUp$. It records the displayed point classifier, distance observations, and metric-law ledger used by every neighborhood request.
\item $T$ is the finite tail-event schedule. Each row names a filter event requested around the target point and the finite stage at which that event is inspected.
\item $V$ is the Metric/Real tolerance row. It matches the metric ball or entourage demand around $X$ with the rational and real-facing tolerance data read by the convergence request.
\item $E$ is the $\RealUp$ seal row. It is available only after the filter row, target point row, tail schedule, and tolerance row have all been displayed.
\item $H$ records componentwise $\hsame$ transport for $B,X,T,V,E$ and for the structural rows below.
\item $C$ records displayed $\Cont$ replay from filterbase refinement to tail events, from target-point neighborhoods to tolerance windows, and from tolerance windows to the Real seal.
\item $P$ is the $\Pkg$ provenance over $\FilterConvergenceUp$, $\CauchyFilterUp$, $\RegularCauchyFilterUp$, $\StreamNameUp$, $\MetricUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FilterConvergenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,X,T,V,E,H,C,P,N$. There is no coordinate for quotient filters, selected host limits, hidden cofinal tails, countable-choice schedules, host equality of target points, or an ambient completeness theorem.
\end{definition}

\begin{theorem}[FilterConvergence NameCert obligations]
\label{thm:filter-convergence-namecert-obligations}
For every accepted $\FilterConvergenceUp$ carrier $F=(B,X,T,V,E,H,C,P,N)$, the local $\NameCert_{\FilterConvergenceUp}$ surface consists exactly of carrier admission, visible filter exposure through $B$, target-point exposure through $X$, finite tail-event exposure through $T$, Metric/Real tolerance readback through $V$, terminal Real seal handoff through $E$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $N$.

These obligations bind the convergence route
$$
\CauchyFilterUp \longmapsto \MetricUp \longmapsto \StreamNameUp \longmapsto \RealUp
$$
without adding quotient filters, selected limits, hidden cofinal tails, countable choice, host target equality, or ambient real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:filter-convergence-carrier}. The packet exposes exactly the visible filter row, target point row, tail-event schedule, tolerance row, Real seal, and structural rows.

The filter and target rows are read first. The row $B$ supplies only finite filterbase requests, while $X$ supplies the metric target point and its displayed neighborhood observations.

The tail schedule and tolerance row then bind convergence to finite data. The schedule $T$ lists the filter events inspected around $X$, and $V$ ties each such event to the Metric and Real tolerance windows consumed by the request.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name the same ordered route. Since the excluded objects are absent from the carrier, no further local NameCert obligation can be exported.
\end{proof}

\begin{theorem}[FilterConvergence tail stability]
\label{thm:filter-convergence-tail-stability}
Let $F=(B,X,T,V,E,H,C,P,N)$ be an accepted $\FilterConvergenceUp$ carrier. Any two displayed tail events in $T$ that are read around the same target point row $X$ admit a later displayed filterbase refinement inside $B$ whose Metric/Real tolerance data is still the row $V$ and whose terminal seal is still $E$.

Consequently tail refinement is stable under componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming through $H,C,P,N$. The stability claim does not use quotient filters, selected host limits, countable choice, hidden cofinal tails, host target equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with two tail events in the finite schedule $T$. Because both events are carrier rows, they are already tied to the same visible filterbase row $B$ and the same target point row $X$.

Use the directed refinement surface read from $B$. The later filterbase row is displayed inside the packet, so the proof never passes to an external cofinal family or quotient filter.

Read the tolerance row next. The row $V$ is the only Metric/Real tolerance interface attached to the scheduled tail events, and $H,C$ transport and replay that same interface to the later refinement.

The Real seal is therefore unchanged. Since $E$ is downstream from $B,X,T,V$, and $P,N$ only source and name those coordinates, the excluded choice, limit, hidden-tail, equality, and completeness principles cannot enter the tail-stability route.
\end{proof}

\begin{theorem}[FilterConvergence Real seal handoff]
\label{thm:filter-convergence-real-seal-handoff}
Every completion-facing or Real-facing consumer of an accepted $\FilterConvergenceUp$ packet must read the displayed convergence route
$$
B \longmapsto X \longmapsto T \longmapsto V \longmapsto E
$$
before the Real seal is available. In BEDC terms, the consumer passes through the visible $\CauchyFilterUp$ row, the target $\MetricUp$ point row, the $\StreamNameUp$ tail-event schedule, and the Metric/Real tolerance row before it reaches $\RealUp$.

The handoff supplies a finite convergence interface for $\RegularCauchyFilterUp$ and downstream completion-limit uniqueness arguments. It supplies no quotient filter, selected host limit, countable-choice schedule, hidden cofinal tail, host equality of target points, or ambient real-completeness principle.
\end{theorem}
\begin{proof}
Start with the visible filter row $B$. A consumer can inspect only the finite filterbase requests and refinements recorded by the packet.

Next read the target and schedule rows. The row $X$ supplies the metric target point and neighborhood observations, while $T$ records the finite tail events that answer those neighborhood requests.

The tolerance and seal rows are downstream. The row $V$ matches those tail events with the Metric and Real tolerance windows, and $E$ seals the compatible readback only after that route has been replayed.

Thus every Real-facing consumer receives the same ordered route through $B,X,T,V,E,H,C,P,N$. Since no excluded principle is a carrier coordinate, the handoff is a finite convergence certificate rather than an ambient completeness assertion.
\end{proof}

\falsifiablePrediction{Every accepted $\FilterConvergenceUp$ read factors through the visible $\CauchyFilterUp$ row, target $\MetricUp$ point row, finite tail-event schedule, Metric/Real tolerance row, $\RealUp$ seal, componentwise transport, continuation replay, provenance, and local $\NameCert$ before any completion-facing consumer reads convergence data.}

\independenceWitness{cauchyfilter, regularcauchyfilter, streamname, metric, real: $\FilterConvergenceUp$ is not bijective to any listed sibling because it jointly carries a visible filter row, target point row, finite tail-event schedule, Metric/Real tolerance row, Real seal, transport, replay, provenance, and local naming.}

\closureat{FilterConvergenceUp}{seedStr}

\begin{closurestatus}{\FilterConvergenceUp}
  \constructivestory{A $\FilterConvergenceUp$ packet is generated from a visible CauchyFilter row, a target Metric point row, a finite StreamName tail-event schedule, a Metric/Real tolerance row, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:filter-convergence-carrier}, \autoref{thm:filter-convergence-namecert-obligations}, \autoref{thm:filter-convergence-tail-stability}, and \autoref{thm:filter-convergence-real-seal-handoff} seed the finite convergence interface from visible filter rows and target metric neighborhoods to Real-facing seal data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected host limits, countable choice, hidden cofinal tails, host target equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, visible filter exposure, target-point exposure, finite tail-event exposure, Metric/Real tolerance readback, Real seal handoff, transport stability, replay stability, and ledger non-escape for BEDC.Derived.FilterConvergenceUp.}
\end{closurestatus}
