\chapter{A Concrete Naming Certificate for $\UniformConvergenceUp$}
\label{ch:concrete-instances-uniform-convergence-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\UniformConvergenceUp$ packet records uniform tail control before any $\UniformLimitUp$ consumer reads a $\RealUp$ seal. It sits over the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the pointwise limiting surface of \autoref{ch:concrete-instances-pointwise-limit-namecert}, the uniform-limit route of \autoref{ch:concrete-instances-uniformlimit-namecert}, the continuous-map graph rows of \autoref{ch:concrete-instances-continuousmap-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names the generic finite tail ledger used by later completion and limit consumers; it is not a selected limit, a supremum norm construction, countable choice, quotient equality of functions, host completeness, or open-cover compactness.

\begin{definition}[Uniform convergence carrier]
\label{def:uniform-convergence-carrier}
A $\UniformConvergenceUp$ carrier is a finite $\BHist$ packet
$$
U=(F,W,Q,R,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the displayed function-family or sequence source. Each source entry is read only through the finite windows named by the packet.
\item $W$ is the finite $\StreamNameUp$ observation-window ledger. It records the parameter windows, index windows, and tolerance-request windows inspected by the consumer.
\item $Q$ is the $\RegSeqRatUp$ readback row for the displayed finite comparisons attached to $F$ and $W$.
\item $R$ is the $\RealUp$ seal row reached only after the regular rational readback has displayed the scheduled comparisons.
\item $T$ is the uniform tail schedule. For each requested tolerance row it records one threshold row shared by every displayed observation window in $W$.
\item $H$ records componentwise $\hsame$ transport for the source, window ledger, readback, real seal, tail schedule, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any limit-facing consumer request through $F,W,T,Q,R$ in that order.
\item $P$ is the $\Pkg$ provenance over $\UniformConvergenceUp$, $\PointwiseLimitUp$, $\UniformLimitUp$, $\ContinuousMapUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformConvergenceUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these nine rows. Its classifier has no coordinate for a selected limiting function, a host supremum norm, quotient equality of functions, countable choice, ambient completeness, or open-cover compactness.
\end{definition}

\begin{theorem}[Uniform convergence NameCert obligations]
\label{thm:uniform-convergence-namecert-obligations}
For every accepted $\UniformConvergenceUp$ carrier
$$
U=(F,W,Q,R,T,H,C,P,N),
$$
the local $\NameCert_{\UniformConvergenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source row, finite $\StreamNameUp$ observation windows, $\RegSeqRatUp$ readbacks, $\RealUp$ seals, uniform tail schedule, transports, continuations, provenance, and local naming;
\item uniform tail coverage, requiring every requested tolerance row to read the single threshold recorded in $T$ before any limiting read is exposed;
\item real-seal non-escape, requiring every $\RealUp$ seal in $R$ to remain downstream of the readback row $Q$ and the schedule row $T$;
\item $\UniformLimitUp$ handoff, requiring each endpoint-facing consumer to factor through $F,W,Q,R,T,H,C,P,N$ before forming a limiting read;
\item transport and replay stability, requiring $H$ and $C$ to preserve the displayed source, window, readback, seal, and tail rows componentwise;
\item excluded rows, ruling out selected limits, host supremum norms, quotient equality of functions, countable choice, ambient completeness, open-cover compactness, and any hidden pointwise-only threshold.
\end{enumerate}
No uniform-convergence obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Project the accepted packet $U=(F,W,Q,R,T,H,C,P,N)$. The carrier exposes exactly the displayed source, finite observation windows, regular rational readbacks, real seals, uniform tail schedule, and structural rows.

Uniformity is supplied by $T$. A tolerance request first selects a single threshold row in that ledger, and the same row must serve every displayed observation window in $W$ before any readback is admitted.

The real seal is then downstream of the regular rational route. The row $Q$ is the only readback channel attached to the scheduled comparisons, and the seal row $R$ becomes visible only after $Q$ has displayed those comparisons through the tail schedule.

The endpoint handoff follows by the displayed route order. A $\UniformLimitUp$ consumer receives $F,W,T,Q,R$ and then the structural rows $H,C,P,N$; there is no carrier coordinate from which it can read a selected limit, host supremum norm, quotient equality, choice row, ambient completeness theorem, open-cover compactness argument, or pointwise-only threshold.
\end{proof}

\begin{theorem}[Uniform convergence UniformLimit handoff]
\label{thm:uniform-convergence-uniform-limit-handoff}
Every $\UniformLimitUp$ consumer of an accepted $\UniformConvergenceUp$ carrier reads
$$
F,W,Q,R,T,H,C,P,N
$$
before forming the limiting read. Thus the limiting route is forced through the displayed source, finite observation windows, regular rational readbacks, real seals, uniform tail schedule, componentwise transport, continuation replay, provenance, and local naming. It receives no selected limit, host supremum norm, quotient function equality, countable-choice schedule, ambient completeness theorem, open-cover compactness principle, or hidden pointwise-only threshold.
\end{theorem}

\begin{proof}
Start with a limit-facing consumer request. By \autoref{def:uniform-convergence-carrier}, the request first reads the source row $F$ through the finite observation windows $W$.

The uniform tail schedule $T$ then supplies the common threshold for the requested tolerance. The readback row $Q$ is attached to that scheduled comparison, and the real seal row $R$ is reachable only after the readback has displayed it.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since every coordinate available to the consumer occurs in the displayed packet, the limiting read cannot be formed from a selected limit, host supremum norm, quotient function equality, countable-choice schedule, ambient completeness theorem, open-cover compactness principle, or hidden pointwise-only threshold.
\end{proof}

\falsifiablePrediction{An accepted $\UniformConvergenceUp$ consumer that reaches a $\UniformLimitUp$ endpoint or $\RealUp$ seal without first reading $F,W,Q,R,T,H,C,P,N$ refutes the carrier surface.}

\independenceWitness{streamname, regseqrat, pointwise-limit, uniformlimit, continuousmap, real: none is bijective to $\UniformConvergenceUp$ because this packet jointly carries a displayed source, finite observation windows, regular readbacks, real seals, one uniform tail schedule, transport, replay, provenance, and local naming.}

\closureat{UniformConvergenceUp}{seedStr}

\begin{closurestatus}{\UniformConvergenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-convergence-carrier}, \autoref{thm:uniform-convergence-namecert-obligations}, and \autoref{thm:uniform-convergence-uniform-limit-handoff} seed the finite uniform tail ledger over displayed sources, StreamName windows, RegSeqRat readbacks, Real seals, and UniformLimit consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected limits, host supremum norms, quotient equality of functions, countable choice, ambient completeness, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform tail coverage, real-seal non-escape, UniformLimit handoff, transport and replay stability, and excluded-row coverage for BEDC.Derived.UniformConvergenceUp.}
  \constructivestory{A $\UniformConvergenceUp$ packet is generated from a displayed function-family or sequence source, finite StreamName observation windows, RegSeqRat readbacks, RealUp seals, one uniform tail schedule, componentwise hsame transport, displayed Cont replay, provenance, and local naming.}
\end{closurestatus}
