\chapter{A Concrete Naming Certificate for $\LaxMilgramUp$}
\label{ch:concrete-instances-lax-milgram-namecert}
\origin{human}

Following Lax and Milgram and the variational treatment in Evans, the $\LaxMilgramUp$ packet records the finite BEDC surface for coercive variational solvability. It is read as a neighbour of the Hilbert and Sobolev certificates of \autoref{ch:concrete-instances-hilbert-namecert} and \autoref{ch:concrete-instances-sobolev-namecert}, with its pairing row anchored in the bilinear-form chapter \autoref{ch:concrete-instances-bilinform-namecert} and its bounded action surface anchored in \autoref{ch:concrete-instances-boundedlinearoperator-namecert}. The packet names only the displayed variational handoff; it does not add a choice-selected solution operator or an ambient PDE existence theorem.

\begin{definition}[Lax-Milgram carrier]
\label{def:lax-milgram-carrier}
A $\LaxMilgramUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
K=(H,B,F,C,S,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $H$ is the Hilbert/Sobolev domain row, read through the $\HilbertUp$ surface and, when a weak-form PDE consumer is present, through the $\SobolevUp$ weak-derivative ledger;
\item $B$ is the $\BilinFormUp$ row naming the bilinear pairing together with its boundedness and coercivity evidence as finite classifier rows;
\item $F$ is the bounded functional row, read through the same bounded-linear-operator surface used by $\BoundedLinearOperatorUp$ consumers;
\item $C$ records the coercivity and boundedness constants as displayed ledger entries rather than as real-number selectors outside the packet;
\item $S$ is the solution handoff row: it exposes the single variational response row certified by the equation $B(S,v)=F(v)$ for displayed test rows $v$ in $H$;
\item $T$ stores the $\hsame$ transport and $\Cont$ replay rows for the domain, bilinear form, bounded functional, constants, and solution handoff;
\item $P$ is the $\Pkg$ provenance over $\HilbertUp$, $\SobolevUp$, $\BilinFormUp$, $\BoundedLinearOperatorUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\LaxMilgramUp}$ evidence.
\end{enumerate}
The carrier has no coordinate for a choice-selected global inverse, a quotient representative, a completed PDE solution space beyond the cited Sobolev row, or a host theorem asserting existence outside the displayed variational packet.
\end{definition}

\begin{theorem}[Lax-Milgram NameCert obligations]
\label{thm:lax-milgram-namecert-obligations}
The local $\NameCert_{\LaxMilgramUp}$ surface for the carrier of \autoref{def:lax-milgram-carrier} consists of exactly five finite obligations:
\begin{enumerate}
\item domain admission, requiring $H$ to be read through the displayed $\HilbertUp$ row and any weak-form consumer through the $\SobolevUp$ ledger;
\item bilinear-form admission, requiring $B$ to expose only the $\BilinFormUp$ pairing row together with boundedness and coercivity ledger entries;
\item functional admission, requiring $F$ to be read through the bounded functional surface supplied by $\BoundedLinearOperatorUp$;
\item variational handoff exactness, requiring every solution-facing read to pass through $S$ and the displayed equation row $B(S,v)=F(v)$ for admitted test rows $v$;
\item transport and replay stability, requiring $T,P,N$ to preserve the same domain, bilinear, functional, constant, and handoff rows under componentwise $\hsame$, displayed $\Cont$, provenance, and local naming.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier rows. The domain, bilinear form, functional, constant ledger, handoff, transport, provenance, and local naming evidence are the full visible inventory of $K$.

Use the cited sibling certificates for each analytic dependency. The Hilbert and Sobolev rows supply the domain-facing reads, the bilinear-form row supplies the pairing and its boundedness/coercivity classifier, and the bounded-linear-operator surface supplies the functional row.

Finally inspect a solution-facing consumer. It can reach only the handoff row $S$ and the displayed variational equation against admitted test rows. The transport, replay, provenance, and naming rows preserve that finite route and add no external selector.
\end{proof}

\begin{theorem}[Lax-Milgram variational handoff]
\label{thm:lax-milgram-variational-handoff}
Every PDE, Sobolev, Hilbert, or variational consumer of an accepted $\LaxMilgramUp$ packet receives only the displayed route
$$
H \longmapsto B \longmapsto F \longmapsto C \longmapsto S \longmapsto T,P,N .
$$
The consumer may use the certified variational response row and its equation against admitted test rows, but it receives no choice-selected solution operator, no quotient representative, no host inverse map, no ambient compactness principle, and no PDE solution space beyond the finite Sobolev or Hilbert rows already cited.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations. They force any consumer to read the domain, bilinear form, functional, constant ledger, and handoff rows in the order displayed by the carrier.

The Sobolev and Hilbert dependencies identify the domain surface, while the bilinear-form and bounded-linear-operator dependencies identify the pairing and functional surfaces. These reads are certificate rows, not host analytic constructions.

It remains to inspect the handoff. The row $S$ is available only as the variational response named by $B(S,v)=F(v)$ for displayed tests $v$. Since no other solution coordinate is present in the carrier, the listed selector, quotient, inverse, compactness, and ambient PDE objects cannot be exported.
\end{proof}

\begin{theorem}[Lax-Milgram energy-minimizer handoff]
\label{thm:lax-milgram-energy-minimizer-handoff}
An accepted $\LaxMilgramUp$ packet exposes its variational solution row as an energy-minimizer handoff only through the Hilbert/Sobolev domain row of \autoref{ch:concrete-instances-hilbert-namecert} and \autoref{ch:concrete-instances-sobolev-namecert}, the $\BilinFormUp$ coercive pairing row of \autoref{ch:concrete-instances-bilinform-namecert}, and the $\BoundedLinearOperatorUp$ functional row of \autoref{ch:concrete-instances-boundedlinearoperator-namecert}. The handoff is the finite route
$$
H\longmapsto B\longmapsto F\longmapsto C\longmapsto S ,
$$
with $T,P,N$ preserving transport, replay, provenance, and local naming. It exports no selected inverse operator, no quotient representative of a solution class, and no ambient PDE existence theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:lax-milgram-carrier}. The only domain coordinate is $H$, so an energy read starts from the Hilbert row and, for weak-form consumers, the Sobolev ledger named by the sibling chapters.

The energy pairing is then forced through $B$ and $C$. The bilinear-form sibling supplies the coercive pairing row, while the constant ledger records the displayed boundedness and coercivity data. No inverse operator is stored in these rows.

The forcing term is the row $F$ supplied through the bounded-linear-operator surface. The variational response row $S$ can therefore be read as an energy-minimizer handoff only after the domain, pairing, constant, and functional rows have been displayed.

Finally $T,P,N$ transport, source, and name the same finite route. Since the carrier has no coordinate for a selected inverse operator, quotient representative, or ambient PDE existence theorem, none of those objects can be exported by the handoff.
\end{proof}

\closureat{LaxMilgramUp}{seedStr}

\begin{closurestatus}{\LaxMilgramUp}
  \constructivestory{A $\LaxMilgramUp$ packet is generated from a Hilbert or Sobolev domain row, a bilinear-form row with boundedness and coercivity ledgers, a bounded functional row, a solution handoff row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lax-milgram-carrier}, \autoref{thm:lax-milgram-namecert-obligations}, and \autoref{thm:lax-milgram-variational-handoff} seed the finite variational certificate surface consumed by Sobolev, Hilbert, PDE, and bounded-operator routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a choice-selected solution operator, quotient representative, host inverse map, ambient compactness principle, or full PDE existence theorem.}
  \upgradepath{Obligation closure requires checked carrier admission, bilinear boundedness and coercivity rows, bounded functional admission, solution handoff exactness, transport, replay, provenance, and local naming for the displayed packet.}
\end{closurestatus}
