\chapter{A Concrete Naming Certificate for $\CauchyInterleavingCriterionUp$}
\label{ch:concrete-instances-cauchy-interleaving-criterion-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CauchyInterleavingCriterionUp$ packet records the finite criterion by which two regular-Cauchy views may be interleaved before a completion-facing consumer reads either view. It sits over the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, the subsequence criterion of \autoref{ch:concrete-instances-cauchy-subsequence-criterion-namecert}, and the product interleaving route of \autoref{ch:concrete-instances-cauchy-interleaving-product-namecert}. The packet is a displayed interleaving criterion for completion consumers; it is not a quotient stream, not a choice-selected limit, and not an ambient completeness coordinate.

\begin{definition}[Cauchy interleaving criterion carrier]
\label{def:cauchy-interleaving-criterion-carrier}
A $\CauchyInterleavingCriterionUp$ carrier is a finite $\BHist$ packet
$$
I=(S_0,S_1,D_0,D_1,T,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S_0$ and $S_1$ are the two $\StreamNameUp$ finite-window rows whose observations are to be interleaved.
\item $D_0$ and $D_1$ are the $\DyadicRatCoreUp$ tolerance ledgers attached to the two windows.
\item $T$ is the finite selector schedule recording which side is read at each displayed stage.
\item $W$ is the common window-extraction row obtained from the two scheduled sources and their dyadic ledgers.
\item $Q$ is the $\RegSeqRatUp$ readback row reconstructed from the extracted interleaving windows.
\item $E$ is the downstream $\RealUp$ seal boundary available only after $S_0,S_1,D_0,D_1,T,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two stream windows, two dyadic ledgers, selector schedule, extracted window, readback row, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through the same interleaving route.
\item $P$ is the $\Pkg$ provenance over $\CauchyInterleavingCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyInterleavingCriterionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows and their replay paths. It has no coordinate for quotient streams, selected host limits, countable choice, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy interleaving criterion NameCert obligations]
\label{thm:cauchy-interleaving-criterion-namecert-obligations}
For every accepted $\CauchyInterleavingCriterionUp$ carrier $I=(S_0,S_1,D_0,D_1,T,W,Q,E,H,C,P,N)$, the local $\NameCert_{\CauchyInterleavingCriterionUp}$ surface consists exactly of carrier admission, two-sided finite-window exposure, two dyadic tolerance ledgers, finite selector admission, common window extraction, regular readback handoff, Real-seal boundary exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. Every $\BishopCompletionCriterionUp$ or $\RegularCauchyCompletionUniversalUp$ consumer reads only this displayed route and receives no quotient stream, selected representative, host convergence predicate, countable-choice selector, or ambient completeness witness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-interleaving-criterion-carrier}. The rows $S_0,S_1,D_0,D_1,T,W,Q,E,H,C,P,N$ are the complete displayed packet.

The analytic rows first expose the two finite stream windows and their dyadic tolerance ledgers. The selector schedule $T$ then chooses the displayed side at each stage, and the common extraction row $W$ records the finite window actually read by the interleaving consumer.

The regular readback $Q$ and Real seal $E$ are downstream of that extracted route. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite criterion, so no quotient stream or choice-selected limit can enter the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy interleaving criterion window extraction]
\label{thm:cauchy-interleaving-criterion-window-extraction}
Every accepted $\CauchyInterleavingCriterionUp$ packet admits a finite window extraction route
$$
(S_0,S_1,D_0,D_1,T)\longmapsto W\longmapsto Q\longmapsto E\longmapsto(H,C,P,N).
$$
The extracted window $W$ is read from the two displayed $\StreamNameUp$ rows using only the two $\DyadicRatCoreUp$ ledgers and the finite selector schedule $T$. Hence downstream $\RealUp$, $\BishopCompletionCriterionUp$, and regular-Cauchy completion consumers cannot replace the route by a quotient of streams, a selected limit, or an ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:cauchy-interleaving-criterion-namecert-obligations}. They force both source windows and both dyadic ledgers to be visible before the selector schedule can be consumed.

The selector schedule is finite, so each displayed stage chooses one of the two already exposed windows. The common extraction row $W$ records exactly those finite choices, and the regular readback row $Q$ is reached only after $W$ has been displayed.

Finally the Real seal and structural rows replay the same route. Because the carrier has no coordinate for quotient streams, selected representatives, countable choice, host real equality, or ambient completeness, a completion-facing consumer receives only the finite extraction route shown above.
\end{proof}

\closureat{CauchyInterleavingCriterionUp}{seedStr}

\begin{closurestatus}{\CauchyInterleavingCriterionUp}
  \constructivestory{A $\CauchyInterleavingCriterionUp$ packet is generated from two StreamName finite-window rows, two DyadicRatCore tolerance ledgers, a finite selector schedule, an extracted interleaving window, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-interleaving-criterion-carrier}, \autoref{thm:cauchy-interleaving-criterion-namecert-obligations}, and \autoref{thm:cauchy-interleaving-criterion-window-extraction} seed the finite interleaving criterion route for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, quotient-stream equality, selected limits, countable choice, host real equality, ambient Real completeness, or a completed-real binary operation.}
  \upgradepath{Obligation closure requires carrier admission, selector-window coverage, dyadic ledger compatibility, regular readback handoff, Real-seal nonescape, and TasteGate field faithfulness for BEDC.Derived.CauchyInterleavingCriterionUp.}
\end{closurestatus}
