\chapter{A Concrete Naming Certificate for $\AiryFunctionUp$}
\label{ch:concrete-instances-airy-function-namecert}
\origin{human}

Following Airy and Olver on the classical Airy differential equation, the $\AiryFunctionUp$ packet records the finite certificate route by which Airy-function reads are named through a displayed scalar ODE, coefficient recurrences, real-series windows, and terminal real-name seals. It consumes the real endpoint discipline of \autoref{ch:concrete-instances-real-namecert}, the finite partial-sum and tail surface of \autoref{ch:concrete-instances-realseries-namecert}, the ODE source of \autoref{ch:concrete-instances-ode-namecert}, and the Picard local-flow route of \autoref{ch:concrete-instances-picard-lindelof-namecert}. The packet is not a host entire-function primitive, an asymptotic expansion theorem, a selected global solution object, or an ambient analytic-completeness claim.

\begin{definition}[Airy function carrier]
\label{def:airy-function-carrier}
An $\AiryFunctionUp$ carrier is a finite $\BHist$ packet
$$
A=(D,I,K,T,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the scalar ODE row for the Airy equation $y''-xy=0$, read through the local $\OdeUp$ source and its displayed derivative, vector-field, and state-window ledgers.
\item $I$ is the initial-data row. It records the chosen Airy branch by finitely displayed values for $y(0)$ and $y'(0)$, including the branch tags that distinguish the standard $\operatorname{Ai}$ and $\operatorname{Bi}$ reads when such a distinction is requested.
\item $K$ is the coefficient-recurrence row. It records the finite recurrence ledger by which coefficient windows for the Airy power series are generated from $D$ and $I$.
\item $T$ is the $\RealSeriesUp$ term-stream row, listing the finite partial-sum windows, tail requests, and shared threshold rows used by the requested Airy read.
\item $S$ is the local Picard or ODE nonescape row, ensuring that the inspected series and flow windows stay inside the displayed scalar state window supplied by $\PicardLindelofUp$.
\item $R$ is the $\RegSeqRatUp$ readback row for coefficients, partial sums, initial values, and endpoint requests.
\item $E$ is the terminal $\RealUp$ seal row reached only after the ODE, initial-data, recurrence, series, nonescape, and readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the ODE row, initial data, recurrence ledger, series windows, nonescape row, readbacks, Real seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from an Airy request through the ODE row, initial data, coefficient recurrence, real-series windows, Picard nonescape, regular readbacks, and the Real seal.
\item $P$ is the $\Pkg$ provenance over $\AiryFunctionUp$, $\OdeUp$, $\PicardLindelofUp$, $\RealSeriesUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AiryFunctionUp}$ row.
\end{enumerate}
The carrier exports only this finite route. It has no coordinate for a host entire function, global analytic continuation, asymptotic sector decomposition, selected zero set, quotient function equality, or ambient completeness theorem.
\end{definition}

\begin{theorem}[Airy function NameCert obligations]
\label{thm:airy-function-namecert-obligations}
For every accepted $\AiryFunctionUp$ carrier $A=(D,I,K,T,S,R,E,H,C,P,N)$, the local $\NameCert_{\AiryFunctionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed ODE, initial-data, recurrence, real-series, nonescape, readback, Real-seal, transport, replay, provenance, and local naming rows;
\item ODE compatibility, requiring $D$ to be the only scalar Airy equation row read by the packet;
\item initial-data compatibility, requiring $I$ to supply the branch-determining values consumed by the recurrence ledger;
\item recurrence exactness, requiring $K$ to generate every inspected coefficient window from $D$ and $I$ before any series read is exposed;
\item real-series visibility, requiring $T$ to expose partial sums, tail thresholds, and endpoint requests only through the $\RealSeriesUp$ surface;
\item local-flow nonescape, requiring $S$ to bind the inspected ODE and series windows to the Picard local-flow route;
\item endpoint sealing, requiring $R$ and $E$ to read every requested coefficient, partial sum, and Airy endpoint through $\RegSeqRatUp$ and $\RealUp$ rows;
\item structural preservation, requiring $H,C,P,N$ to transport, replay, source, and name exactly the displayed rows and no external analytic object.
\end{enumerate}
No Airy-function obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:airy-function-carrier}. The ODE row $D$ and initial-data row $I$ are visible before any recurrence or series row can be inspected, so the requested branch is fixed inside the packet.

The coefficient and series obligations are then finite ledger checks. The recurrence row $K$ supplies the inspected coefficient windows, and the $\RealSeriesUp$ row $T$ supplies only the partial sums, tail thresholds, and endpoint requests listed in the packet.

The local-flow and endpoint rows close the analytic route. The nonescape row $S$ keeps the inspected windows inside the displayed Picard or ODE state window, while $R$ and $E$ provide regular rational readback and the terminal real-name seal.

Finally $H,C,P,N$ transport, replay, source, and name the same finite data. Since the carrier has no coordinate for a host entire function, asymptotic sector, selected zero set, quotient function equality, or ambient completeness theorem, the local NameCert surface has no obligation row for such an object.
\end{proof}

\begin{theorem}[Airy function real-series handoff]
\label{thm:airy-function-real-series-handoff}
Every Real-facing read from an accepted $\AiryFunctionUp$ carrier factors through
$$
D,I \longmapsto K \longmapsto T,S \longmapsto R,E \longmapsto H,C,P,N .
$$
Thus a consumer receives the displayed Airy ODE row, branch initial data, coefficient recurrence ledger, finite real-series windows, local nonescape row, regular readback, and terminal real seal, but receives no host entire-function primitive or global analytic continuation datum.
\end{theorem}
\begin{proof}
Start with an accepted packet $A=(D,I,K,T,S,R,E,H,C,P,N)$. The only ODE and branch data available to a consumer are $D$ and $I$, so a Real-facing read begins at the displayed Airy equation and its carried initial values.

The recurrence row $K$ is the next forced coordinate. It generates the inspected coefficient windows from the ODE and branch data before the $\RealSeriesUp$ row $T$ exposes partial sums or tail thresholds.

The nonescape and endpoint rows are downstream. The row $S$ keeps the displayed series and local-flow windows inside the accepted ODE route, and $R,E$ provide the regular readback and terminal $\RealUp$ seal.

The structural rows $H,C,P,N$ preserve and name only that route. Hence the handoff cannot introduce a host entire function, a global continuation object, an asymptotic sector decomposition, a selected zero set, or quotient function equality.
\end{proof}

\falsifiablePrediction{Every $\AiryFunctionUp$ read factors through one displayed Airy ODE row, one branch initial-data row, one coefficient-recurrence ledger, one $\RealSeriesUp$ partial-sum and tail surface, one Picard nonescape row, one $\RegSeqRatUp$ readback row, one $\RealUp$ endpoint seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}

\independenceWitness{real, realseries, ode, picard-lindelof: $\AiryFunctionUp$ is not bijective to any listed sibling because it jointly carries an Airy ODE row, branch initial data, coefficient recurrence, real-series windows, local-flow nonescape, regular readback, Real sealing, transport, replay, provenance, and local naming.}

\closureat{AiryFunctionUp}{seedStr}

\begin{closurestatus}{\AiryFunctionUp}
  \constructivestory{An $\AiryFunctionUp$ packet is generated from a displayed Airy ODE row, branch initial data, coefficient-recurrence ledger, RealSeriesUp partial-sum and tail rows, Picard nonescape data, RegSeqRat readbacks, RealUp endpoint seals, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:airy-function-carrier}, \autoref{thm:airy-function-namecert-obligations}, and \autoref{thm:airy-function-real-series-handoff} seed the finite Airy-function certificate surface over displayed ODE, branch, recurrence, series, nonescape, readback, and real endpoint rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host entire functions, global analytic continuation, asymptotic expansions, selected zero sets, quotient function equality, ambient analytic completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, ODE compatibility, branch-data compatibility, recurrence exactness, real-series visibility, nonescape, endpoint sealing, and structural preservation for BEDC.Derived.AiryFunctionUp.}
\end{closurestatus}
