\chapter{A Concrete Naming Certificate for $\FredholmAlternativeUp$}
\label{ch:concrete-instances-fredholm-alternative-namecert}
\origin{human}

Following Fredholm, Riesz, and compact-operator treatments of linear equations, the $\FredholmAlternativeUp$ packet records the finite BEDC surface for the kernel--range obstruction alternative attached to a displayed compact perturbation. It is read after the compact-operator certificate of \autoref{ch:concrete-instances-compactoperator-namecert}, the Banach and Hilbert carrier rows of \autoref{ch:concrete-instances-banach-namecert} and \autoref{ch:concrete-instances-hilbert-namecert}, the bounded-operator action surface of \autoref{ch:concrete-instances-boundedlinearoperator-namecert}, the separation witness of \autoref{ch:concrete-instances-riesz-lemma-namecert}, and the variational handoff of \autoref{ch:concrete-instances-lax-milgram-namecert}. The packet names only this displayed finite alternative route; it does not import a host Fredholm theorem, a quotient index equality, a choice-selected inverse, or an ambient spectral decomposition.

\begin{definition}[Fredholm alternative carrier]
\label{def:fredholm-alternative-carrier}
A $\FredholmAlternativeUp$ carrier is a finite $\BHist$ packet
$$
F=(S,T,B,K,L,V,R,A,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $S$ is the source endpoint row, read through the $\BanachUp$ and, when an orthogonal witness is present, $\HilbertUp$ certificate surfaces;
\item $T$ is the target endpoint row, read through the same Banach or Hilbert certificate discipline;
\item $B$ is the $\BoundedLinearOperatorUp$ row naming the displayed linear action and norm-bound ledger between $S$ and $T$;
\item $K$ is the $\CompactOperatorUp$ row naming the compact perturbation witness by finite image-net schedules and tail moduli;
\item $L$ is the $\LaxMilgramUp$ or bounded-action handoff row used by variational consumers that read the same operator boundary;
\item $V$ is the $\RieszLemmaUp$ separation row available when a range-obstruction witness is exposed;
\item $R$ is the kernel witness row, recording the finite nonzero-kernel or kernel-refusal evidence attached to the displayed operator equation;
\item $A$ is the range-obstruction witness row, recording the finite cokernel-facing obstruction, separation functional, or refusal of surjectivity over the same endpoints;
\item $H$ stores componentwise $\hsame$ transport for the endpoint, bounded-action, compactness, variational, separation, kernel, and obstruction rows;
\item $C$ stores displayed $\Cont$ replay for the same rows;
\item $P$ is the $\Pkg$ provenance over $\FredholmAlternativeUp$, $\CompactOperatorUp$, $\BanachUp$, $\HilbertUp$, $\BoundedLinearOperatorUp$, $\RieszLemmaUp$, $\LaxMilgramUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\FredholmAlternativeUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host inverse, quotient-space equality, index formula, selected basis of the kernel, selected complement of the range, or external spectral theorem.
\end{definition}

\begin{theorem}[Fredholm alternative NameCert obligations]
\label{thm:fredholm-alternative-namecert-obligations}
For the carrier of \autoref{def:fredholm-alternative-carrier}, the local $\NameCert_{\FredholmAlternativeUp}$ surface consists of exactly six finite obligations:
\begin{enumerate}
\item endpoint admission through the displayed $\BanachUp$ or $\HilbertUp$ source and target rows;
\item bounded-action admission through the $\BoundedLinearOperatorUp$ row $B$;
\item compact-perturbation admission through the $\CompactOperatorUp$ row $K$;
\item alternative-witness exposure, requiring the kernel witness $R$ or the range-obstruction witness $A$ to be read as displayed finite rows over the same endpoints;
\item separation and variational compatibility, requiring $V$ and $L$ to support only the displayed obstruction or handoff route already present in the carrier;
\item transport, replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier rows. The endpoint, bounded-action, compactness, variational, separation, kernel, obstruction, transport, replay, provenance, and local naming entries are the full visible inventory of $F$.

Read the analytic dependencies next. The Banach or Hilbert rows determine the endpoints, the bounded-operator row determines the action, and the compact-operator row supplies the finite compactness witness. These rows name BEDC certificate data rather than a host operator theorem.

The alternative witness is then local to the displayed packet. If the kernel side is exposed, it is exposed through $R$; if the range-obstruction side is exposed, it is exposed through $A$ together with the separation row $V$. The variational row $L$ is only a handoff through the same bounded-action surface.

Finally $H,C,P,N$ preserve this finite route. Since the carrier contains no additional inverse, quotient, index, complement, or spectral coordinate, the six obligations exhaust the local $\NameCert_{\FredholmAlternativeUp}$ surface.
\end{proof}

\begin{theorem}[Fredholm alternative kernel--cokernel handoff]
\label{thm:fredholm-alternative-kernel-cokernel-handoff}
Let
$$
F=(S,T,B,K,L,V,R,A,H,C,P,N)
$$
be an accepted $\FredholmAlternativeUp$ packet. Every consumer that reads a kernel-facing conclusion or a range-obstruction conclusion must pass through the same endpoint rows $S,T$, bounded-action row $B$, compact-operator row $K$, separation or variational handoff rows $V,L$, transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$. The handoff exposes the displayed kernel witness $R$ or the displayed range-obstruction witness $A$; it exposes no host inverse, quotient equality, Fredholm index, selected kernel basis, selected range complement, or ambient spectral theorem.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:fredholm-alternative-namecert-obligations}. They force endpoint admission, bounded-action admission, compact-perturbation admission, and witness exposure to be read from one finite packet.

If a consumer follows the kernel side, the only available kernel-facing row is $R$, and it is transported by the same $H,C,P,N$ rows as the operator and compactness data. If a consumer follows the range-obstruction side, the obstruction row is $A$, with the separation support $V$ and the variational handoff $L$ read through the same endpoints.

Thus the two readings are not detached alternatives living over different carriers. They are the two witness exits of one finite route over $S,T,B,K,L,V,H,C,P,N$. The excluded inverse, quotient, index, basis, complement, and spectral objects are absent from the carrier and therefore cannot be exported by the handoff.
\end{proof}

\closureat{FredholmAlternativeUp}{seedStr}

\begin{closurestatus}{\FredholmAlternativeUp}
  \constructivestory{A $\FredholmAlternativeUp$ packet is generated from Banach or Hilbert endpoint rows, a bounded-operator row, a compact-operator row, variational and separation handoff rows, kernel and range-obstruction witnesses, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:fredholm-alternative-carrier}, \autoref{thm:fredholm-alternative-namecert-obligations}, and \autoref{thm:fredholm-alternative-kernel-cokernel-handoff} seed the finite Fredholm-alternative certificate surface consumed by compact-operator, Banach, Hilbert, bounded-operator, Riesz-separation, and Lax-Milgram routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host Fredholm theorem, quotient-space equality, index formula, selected inverse, selected kernel basis, selected range complement, or standard bridge.}
  \upgradepath{Obligation closure requires checked endpoint admission, bounded-action admission, compact-perturbation admission, kernel witness exposure, range-obstruction exposure, separation and variational compatibility, transport, replay, provenance, and local naming for the displayed packet.}
\end{closurestatus}
