\chapter{A Concrete Naming Certificate for $\LimitComparisonTestUp$}
\label{ch:concrete-instances-limit-comparison-test-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and Hardy's classical comparison-test presentation, the $\LimitComparisonTestUp$ packet records the finite route by which a source sequence is compared to a positive comparator sequence before a real-facing conclusion is exposed. It is the sequence-level sibling of \autoref{ch:concrete-instances-series-limit-comparison-namecert}: $\SeriesLimitComparisonUp$ consumes the resulting comparison surface for series tails, while $\LimitComparisonTestUp$ names the underlying ratio-test carrier over $\StreamNameUp$ windows from \autoref{ch:concrete-instances-streamname-namecert}, $\RegSeqRatUp$ readback from \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The packet exposes finite ratio-control data; it does not import a host quotient limit, quotient stream equality, real trichotomy, countable choice, or ambient completeness.

\begin{definition}[Limit comparison test carrier]\label{def:limit-comparison-test-carrier}
A $\LimitComparisonTestUp$ carrier is a finite $\BHist$ packet
$$
L=(S,T,W_S,W_T,Q_S,Q_T,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\StreamNameUp$ row, exposing exactly the inspected finite windows of the sequence being tested.
\item $T$ is the comparator $\StreamNameUp$ row, exposing exactly the matched finite windows of the positive comparator sequence.
\item $W_S$ and $W_T$ are the source and comparator observation schedules used by downstream sequence and series consumers.
\item $Q_S$ and $Q_T$ are the $\RegSeqRatUp$ readback rows attached to the displayed source and comparator windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, carrying the ratio slack, positivity margin, comparison radius, and endpoint tolerance consumed by the test.
\item $R$ is the eventual positive ratio ledger. It displays a finite threshold after which comparator observations are positive and source-to-comparator comparisons remain inside the dyadic band recorded in $D$.
\item $E$ is the $\RealUp$ seal reached only after the source windows, comparator windows, regular readbacks, dyadic ledger, and ratio ledger have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source windows, comparator windows, readback rows, dyadic ledger, ratio ledger, real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a limit-comparison request through $S,T,W_S,W_T,Q_S,Q_T,D,R$ and then to the real-facing seal $E$.
\item $P$ is the $\Pkg$ provenance over $\LimitComparisonTestUp$, $\SeriesLimitComparisonUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LimitComparisonTestUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed tuple $S,T,W_S,W_T,Q_S,Q_T,D,R,E,H,C,P,N$. It has no coordinate for a host quotient limit, quotient stream equality, a selected infinite tail, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.
\end{definition}

\begin{theorem}[Limit comparison test NameCert obligations]\label{thm:limit-comparison-test-namecert-obligations}
For every accepted $\LimitComparisonTestUp$ carrier $L=(S,T,W_S,W_T,Q_S,Q_T,D,R,E,H,C,P,N)$, the local $\NameCert_{\LimitComparisonTestUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed source windows, comparator windows, readback rows, dyadic tolerance ledger, eventual positive ratio ledger, real seal, transport, replay, provenance, and local naming rows;
\item source-window exactness, requiring every inspected source observation to pass through $S,W_S,Q_S,D$ before the ratio ledger is read;
\item comparator-window exactness, requiring every inspected comparator observation to pass through $T,W_T,Q_T,D$ before positivity or ratio control is used;
\item eventual positivity, requiring $R$ to display the finite threshold and positive comparator margin used by all later comparisons;
\item ratio-band exactness, requiring $R$ and $D$ to display the dyadic lower and upper comparison bounds before any real-facing seal is consumed;
\item real-seal nonescape, requiring $E$ to be downstream of the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and ratio-ledger rows and to export no host quotient limit, quotient stream equality, selected tail, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge datum;
\item componentwise transport, displayed replay, provenance, and local naming for the same finite route through $H,C,P,N$.
\end{enumerate}
No limit-comparison-test obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $L=(S,T,W_S,W_T,Q_S,Q_T,D,R,E,H,C,P,N)$. The carrier definition exposes the source and comparator windows, their regular readbacks, the shared dyadic ledger, the eventual positive ratio ledger, and the structural rows.

The source side and comparator side are read separately. Source observations must pass through $S,W_S,Q_S,D$, while comparator observations must pass through $T,W_T,Q_T,D$.

The ratio ledger $R$ then supplies the finite positivity threshold and dyadic comparison band. Since these are displayed rows, a consumer cannot replace them by a host quotient limit or by an undisplayed infinite tail.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name the same route. Because no excluded analytic or choice object appears as a carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Limit comparison test Cauchy handoff]\label{thm:limit-comparison-test-cauchy-handoff}
Let $L=(S,T,W_S,W_T,Q_S,Q_T,D,R,E,H,C,P,N)$ be an accepted $\LimitComparisonTestUp$ carrier. Every Cauchy-facing or series-facing read of the source route factors through
$$
T,W_T,Q_T,D \longmapsto R \longmapsto S,W_S,Q_S,D \longmapsto E,H,C,P,N .
$$
Thus comparator control is handed to the source route only through the displayed eventual positive ratio ledger and dyadic tolerance budget. The handoff exports finite BEDC comparison data, not a host quotient limit, quotient stream equality, selected tail, countable choice, real trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a Cauchy-facing or series-facing request for the source route. The comparator data available to the carrier are exactly $T,W_T,Q_T,D$, so the request first reads the displayed comparator windows, readback row, and tolerance ledger.

The ledger $R$ supplies the finite threshold, positivity margin, and dyadic ratio band that connect later comparator observations to later source observations. This is a packet row rather than a host convergence assertion.

The request then returns to the source rows $S,W_S,Q_S,D$. These rows expose the finite source windows and regular rational readbacks that a downstream $\SeriesLimitComparisonUp$ or Cauchy consumer may inspect.

The real seal and structural rows $E,H,C,P,N$ preserve that finite route. Since the carrier has no coordinate for quotient limits, quotient streams, choice, trichotomy, or ambient completeness, every such handoff is exhausted by the displayed packet.
\end{proof}

\closureat{LimitComparisonTestUp}{seedStr}

\begin{closurestatus}{\LimitComparisonTestUp}
  \constructivestory{A $\LimitComparisonTestUp$ packet is generated from source and comparator StreamName windows, RegSeqRat readback rows, a DyadicRatCore tolerance ledger, an eventual positive ratio ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:limit-comparison-test-carrier}, \autoref{thm:limit-comparison-test-namecert-obligations}, and \autoref{thm:limit-comparison-test-cauchy-handoff} seed the finite constructive limit-comparison route from positive comparator windows through ratio budgeting to source-route RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host quotient limits, quotient stream equality, selected tails, countable choice, real trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source and comparator window exactness, eventual positive ratio-ledger stability, DyadicRatCore and RegSeqRat budget handoff, Real seal nonescape, and TasteGate field faithfulness for BEDC.Derived.LimitComparisonTestUp.}
\end{closurestatus}
