\chapter{A Concrete Naming Certificate for $\OperatorNormUp$}
\label{ch:concrete-instances-operator-norm-namecert}
\origin{human}

Following Bishop and standard functional analysis, the $\OperatorNormUp$ packet records the finite BEDC surface by which a displayed bounded linear operator exposes a scalar norm-bound ledger. It sits over the functional-analysis interface of \autoref{ch:concrete-instances-functionalanalysis-namecert}, the bounded-operator rows of \autoref{ch:concrete-instances-boundedlinearoperator-namecert}, the scalar boundary of \autoref{ch:concrete-instances-real-namecert}, the Banach-algebra norm discipline of \autoref{ch:concrete-instances-banachalgebra-namecert}, and the downstream radius consumer of \autoref{ch:concrete-instances-spectral-radius-namecert}. The packet names the operator norm as certificate data, not as a host supremum, selected extremal vector, quotient equality of maps, or unrestricted completeness principle.

\begin{definition}[Operator norm carrier]
\label{def:operator-norm-carrier}
For a displayed $\BoundedLinearOperatorUp$ row $T$, an $\OperatorNormUp(T)$ carrier is a finite $\BHist$ packet
$$
O=(T,R,B,W,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the source bounded-linear-operator row, including its displayed domain, target, action, linearity, and boundedness ledger.
\item $R$ is the $\RealUp$ scalar interface used to read norm-bound endpoints.
\item $B$ is the finite bound ledger: each inspected source-radius window is paired with a displayed scalar bound for the corresponding operator image.
\item $W$ is the operator-norm witness row, recording the chosen scalar endpoint that dominates the displayed bound ledger.
\item $L$ is the local stability row saying that any downstream read of the operator-norm endpoint must use the same bounded-operator row $T$ and the same $\RealUp$ bound interface $R$.
\item $H$ records componentwise $\hsame$ transport for the operator row, scalar row, bound ledger, norm witness, stability row, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a bounded-operator request through $T,R,B,W,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\OperatorNormUp$, $\FunctionalAnalysisUp$, $\BoundedLinearOperatorUp$, $\RealUp$, $\BanachAlgebraUp$, $\SpectralRadiusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\OperatorNormUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,R,B,W,L,H,C,P,N$. It has no coordinate for a host supremum over all unit vectors, an attained norm vector, quotient equality of bounded maps, a completed operator algebra, countable choice, or a spectral-radius conclusion.
\end{definition}

\begin{theorem}[Operator norm NameCert obligations]
\label{thm:operator-norm-namecert-obligations}
For every accepted $\OperatorNormUp(T)$ carrier $O=(T,R,B,W,L,H,C,P,N)$, the local $\NameCert_{\OperatorNormUp}$ surface consists exactly of carrier admission for the bounded-operator row, scalar RealUp interface, finite bound ledger, operator-norm witness row, stability row, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. A downstream consumer may inspect the displayed endpoint $W$ only through the source row $T$ and the scalar row $R$ already stored in the carrier.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:operator-norm-carrier}. The analytic coordinates are $T,R,B,W,L$, and the structural coordinates are $H,C,P,N$.

Carrier admission exposes the bounded-operator row $T$ before any norm endpoint is public. The scalar row $R$ fixes the RealUp interface, while $B$ records the finite image-bound ledger and $W$ records the endpoint that dominates those displayed rows.

The stability row $L$ binds the endpoint read back to the same operator and scalar interface. Componentwise transport through $H$ and replay through $C$ preserve that route, while $P,N$ source and name the certificate.

Since no remaining field is available, the local NameCert surface cannot export a host supremum, an attained norm vector, quotient map equality, countable choice, or an independent spectral-radius fact.
\end{proof}

\begin{theorem}[Operator norm stability obligation]
\label{thm:operator-norm-stability-obligation}
Every accepted $\OperatorNormUp(T)$ read that is consumed by $\FunctionalAnalysisUp$, $\BanachAlgebraUp$, or $\SpectralRadiusUp$ factors through the same displayed bounded-operator row $T$, scalar interface $R$, finite bound ledger $B$, norm endpoint $W$, stability row $L$, and structural rows $H,C,P,N$. Thus a consumer cannot change the operator, scalar carrier, or bound ledger while retaining the same local operator-norm certificate.
\end{theorem}
\begin{proof}
Begin with an accepted operator-norm read. By \autoref{thm:operator-norm-namecert-obligations}, the endpoint $W$ is available only after $T,R,B$ have been displayed.

The stability row $L$ is the only row that licenses downstream reuse. It names the source operator and scalar interface together with the bound ledger, so a FunctionalAnalysis, BanachAlgebra, or SpectralRadius consumer receives the same data that the local certificate admitted.

Transport and replay do not add coordinates. They carry $T,R,B,W,L$ componentwise and then return to the same provenance and naming rows. Therefore changing the operator, scalar carrier, or bound ledger changes the packet classifier rather than preserving the certificate.
\end{proof}

\begin{theorem}[Operator norm Real-bound handoff]
\label{thm:operator-norm-real-bound-handoff}
Every Real-facing consumer of an accepted $\OperatorNormUp(T)$ packet receives a finite handoff
$$
\BoundedLinearOperatorUp,\quad \RealUp,\quad \BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert
$$
in which the exported datum is the displayed scalar endpoint $W$ attached to the ledger $B$. The handoff does not supply a host supremum, an attained norm vector, a quotient of bounded maps, or a completed Banach-algebra norm object.
\end{theorem}
\begin{proof}
Read the route from \autoref{def:operator-norm-carrier}. The Real-facing endpoint is $W$, and it is attached to the ledger $B$ over the scalar interface $R$.

The bounded-operator row $T$ is inspected first. Only then can the scalar endpoint and the stability row be replayed through $H,C,P,N$.

The exported object is therefore a finite RealUp bound row. No carrier field names a supremum over all unit vectors, an attaining vector, a quotient map, or an ambient Banach-algebra completion.
\end{proof}

\begin{theorem}[Operator norm nonescape]
\label{thm:operator-norm-nonescape}
No accepted $\OperatorNormUp(T)$ packet exports spectral radius, compact-operator spectrum, host operator equality, selected extremal vector, quotient completion, or countable choice. Any such consumer must provide its own displayed rows in addition to the operator-norm packet.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its fields are exactly $T,R,B,W,L,H,C,P,N$.

The first five fields name the bounded-operator route, scalar route, finite bound ledger, endpoint, and stability obligation. The last four fields transport, replay, source, and name those rows.

None of these fields is a spectral-radius row, compact-spectrum row, host equality predicate, extremal-vector selector, quotient-completion row, or choice schedule. Hence every consumer needing one of those objects must supply it outside the operator-norm certificate.
\end{proof}

\falsifiablePrediction{Every accepted $\OperatorNormUp$ consumer exposes the same $\BoundedLinearOperatorUp$ row, $\RealUp$ scalar interface, finite bound ledger, norm endpoint, stability row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row before any operator-norm conclusion is public.}

\independenceWitness{functionalanalysis, boundedlinearoperator, real, banachalgebra, spectral-radius: FunctionalAnalysisUp gives the ambient analytic interface; BoundedLinearOperatorUp gives action and boundedness rows; RealUp gives scalar endpoints; BanachAlgebraUp gives product-norm discipline; SpectralRadiusUp consumes power-norm rows. None is bijective to the packet that jointly records the operator-norm bound ledger, stability row, handoff, transport, replay, provenance, and local naming.}

\closureat{OperatorNormUp}{seedStr}

\begin{closurestatus}{\OperatorNormUp}
  \constructivestory{An $\OperatorNormUp$ packet is generated from a bounded-linear-operator row, a RealUp scalar interface, a finite bound ledger, an operator-norm endpoint, a stability row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:operator-norm-carrier}, \autoref{thm:operator-norm-namecert-obligations}, \autoref{thm:operator-norm-stability-obligation}, \autoref{thm:operator-norm-real-bound-handoff}, and \autoref{thm:operator-norm-nonescape} seed the finite operator-norm route over FunctionalAnalysisUp, BoundedLinearOperatorUp, RealUp, BanachAlgebraUp, SpectralRadiusUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host suprema over all unit vectors, attained norm vectors, quotient equality of bounded maps, completed operator algebras, spectral-radius identities, compact-operator spectral theory, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite bound-ledger exactness, stability through downstream consumers, Real-bound handoff, structural transport, replay, provenance, and nonescape for BEDC.Derived.OperatorNormUp.}
\end{closurestatus}
