\chapter{A Concrete Naming Certificate for $\HeineCantorUp$}
\label{ch:concrete-instances-heine-cantor-namecert}
\origin{human}

Following Bishop and Bridges, the $\HeineCantorUp$ packet records compact-metric uniform-modulus extraction as finite NameCert data. It reads the finite-net surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the endpoint mesh and refinement rows of \autoref{ch:concrete-instances-located-interval-compactness-namecert}, the pointwise modulus rows of \autoref{ch:concrete-instances-continuousmap-namecert}, and the target consumer interface of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The chapter names the constructive route from compact finite data and local continuity rows to one displayed uniform modulus, without importing open-cover compactness, a selected subcover functional, trichotomy on host reals, or ambient completeness.

\begin{definition}[Heine-Cantor carrier]
\label{def:heine-cantor-carrier}
A $\HeineCantorUp$ carrier is a finite $\BHist$ packet
$$
K=(X,Y,F,E,N,R,L,M,T,H,C,P,A)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\CompactMetricUp$ source row, exposing finite $\mathsf{ProbeBundle}$ net rows at the source precision scales consumed by the modulus extraction.
\item $Y$ is the target metric row whose distance ledger receives the final uniform estimate.
\item $F$ is the $\ContinuousMapUp$ row from $X$ to $Y$, including the pointwise modulus rows attached to listed net centers.
\item $E$ is the positive target precision row, read as a $\RealUp$ or $\RegSeqRatUp$ endpoint history when the consumer presents a real tolerance.
\item $N$ is the compact finite-net row selected from $X$ for the scale determined by $E$.
\item $R$ lists the local pointwise radius rows for the centers of $N$, with rational lower-bound readbacks through $\RegSeqRatUp$, $\RealUp$, and the local rational classifier.
\item $L$ is the $\LocatedIntervalCompactnessUp$ mesh and refinement handoff row when the finite-net data is produced from located interval endpoints.
\item $M$ is the exported source modulus row, obtained by the finite fold over the radius rows $R$.
\item $T$ is the target estimate row, combining compact-net coverage, two pointwise estimates around a selected center, and the target metric triangle route.
\item $H$ records componentwise $\hsame$ transport for the compact source, target metric, continuous-map, precision, finite-net, radius, located-interval, modulus, and target-estimate rows.
\item $C$ records the displayed $\Cont$ replay route from compact data and pointwise continuity data to the $\UniformModulusUp$ consumer.
\item $P$ records $\Pkg$ provenance over $\HeineCantorUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\LocatedIntervalCompactnessUp$, $\UniformModulusUp$, $\RealUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, and $\Cont$ rows.
\item $A$ is the local $\NameCert_{\HeineCantorUp}$ row.
\end{enumerate}
The carrier exposes only compact finite-net rows, continuous-map modulus rows, located mesh/refinement rows, endpoint readbacks, componentwise transport, replay, provenance, and local naming. It has no coordinate for arbitrary open covers, selected center choice, host real equality, quotient completion, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Heine-Cantor compact uniform modulus]
\label{thm:heine-cantor-compact-uniform-modulus}
For every accepted $\HeineCantorUp$ carrier
$$
K=(X,Y,F,E,N,R,L,M,T,H,C,P,A),
$$
the exported source row $M$ is a $\UniformModulusUp$ witness for the continuous map row $F$ at target precision $E$. Any consumer of the uniform-modulus witness must factor through the finite route
$$
X,F,E \longmapsto N,R,L \longmapsto M,T \longmapsto H,C,P,A.
$$
Thus compact-metric finite nets, $\ContinuousMapUp$ pointwise modulus rows, $\LocatedIntervalCompactnessUp$ mesh and refinement data, $\RealUp$ and $\RegSeqRatUp$ endpoint readbacks, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ ledger suffice to export the compact uniform modulus.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:heine-cantor-carrier}. The target precision row $E$ determines the compact source scale, and the $\CompactMetricUp$ row $X$ supplies the finite net row $N$ at that scale.

Read the continuous-map row $F$ at each center of $N$. The pointwise radius rows are stored in $R$, and their rational lower-bound readbacks are attached to the $\RegSeqRatUp$ and $\RealUp$ endpoint rows already present in the packet.

When the source net is produced from an interval presentation, the row $L$ supplies the located mesh and finite refinement data of \autoref{ch:concrete-instances-located-interval-compactness-namecert}. This row is a handoff into the compact finite-net route, not a general open-cover compactness principle.

Fold the finite family of radius rows $R$ into the single source row $M$. The fold is finite because it ranges only over the centers listed by $N$, and componentwise transport in $H$ preserves the compact source, continuous-map, endpoint, radius, and folded-modulus rows.

Finally use the target estimate row $T$. Compact-net coverage places two source points near a listed center, the pointwise rows in $R$ estimate their images at that center, and the target metric ledger combines the estimates at precision $E$. Replay by $C$ then presents $M$ to the $\UniformModulusUp$ consumer, while $P$ and $A$ record the provenance and local naming ledger.
\end{proof}

\closureat{HeineCantorUp}{seedStr}

\begin{closurestatus}{\HeineCantorUp}
  \constructivestory{A $\HeineCantorUp$ packet is generated from CompactMetric finite-net rows, ContinuousMap pointwise modulus rows, LocatedIntervalCompactness mesh/refinement rows, RealUp and RegSeqRat endpoint readbacks, a finite radius fold, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:heine-cantor-carrier} and \autoref{thm:heine-cantor-compact-uniform-modulus} seed the compact finite-net route from pointwise continuity data to a UniformModulus consumer.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected subcovers, choice, host real equality, trichotomy, quotient completion, ambient Real completeness, Lean verification, or standard bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net extraction, finite radius fold, target estimate handoff, transport, replay, provenance, and local naming for BEDC.Derived.HeineCantorUp.}
\end{closurestatus}
