\chapter{A Concrete Naming Certificate for $\BishopRealApartnessTopologyUp$}
\label{ch:concrete-instances-bishop-real-apartness-topology-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopRealApartnessTopologyUp$ packet records the finite neighbourhood surface obtained when Bishop real names are read through apartness-positive and located comparison evidence before any topology-facing consumer sees an open-neighbourhood ledger. It sits beside the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the positive separation surface of \autoref{ch:concrete-instances-apartnessreal-namecert}, the located real packet of \autoref{ch:concrete-instances-locatedreal-namecert}, the topology interface of \autoref{ch:concrete-instances-topology-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}. The packet exports a constructive topology route for one displayed Bishop real neighbourhood; it exports no trichotomy, host open set, quotient real equality, countable choice, or ambient completeness.

\begin{definition}[Bishop real apartness topology carrier]
\label{def:bishop-real-apartness-topology-carrier}
A $\BishopRealApartnessTopologyUp$ carrier is a finite $\BHist$ packet
$$
B=(R,A,L,T,W,Q,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ name row, read only through the terminal real-name seal selected for the packet.
\item $A$ is the $\ApartnessRealUp$ positive-evidence row, recording the displayed apartness radius, endpoint readbacks, and positive separation ledger.
\item $L$ is the $\LocatedRealUp$ comparison row, recording the located left/right comparison windows used by the same neighbourhood request.
\item $T$ is the $\TopologyUp$ consumer row, admitting only the topology-facing neighbourhood ledger generated from $A,L,W,Q,O$.
\item $W$ is the shared $\StreamNameUp$ finite-window schedule for the real name, apartness evidence, located comparison, and neighbourhood ledger.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational observations inspected by $R,A,L,W$.
\item $O$ is the open-neighbourhood ledger generated from the apartness-positive evidence and located comparison rows before $T$ is read.
\item $H$ records componentwise $\hsame$ transport for the real name, apartness evidence, located comparison, topology row, stream schedule, regular readback, open-neighbourhood ledger, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Bishop real neighbourhood request through $R,A,L,W,Q,O$ and then to the topology consumer row $T$.
\item $P$ is the $\Pkg$ provenance over $\BishopRealApartnessTopologyUp$, $\RealUp$, $\ApartnessRealUp$, $\LocatedRealUp$, $\TopologyUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BishopRealApartnessTopologyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,A,L,T,W,Q,O,H,C,P,N$. It has no coordinate for trichotomy, host open sets, quotient real equality, countable choice, ambient completeness, or a topology object detached from the displayed open-neighbourhood ledger.
\end{definition}

\begin{theorem}[Bishop real apartness topology NameCert obligations]
\label{thm:bishop-real-apartness-topology-namecert-obligations}
For every accepted $\BishopRealApartnessTopologyUp$ carrier $B=(R,A,L,T,W,Q,O,H,C,P,N)$, the local $\NameCert_{\BishopRealApartnessTopologyUp}$ surface consists exactly of the following finite rows:
\begin{enumerate}
\item carrier admission for the $\RealUp$ name, $\ApartnessRealUp$ positive-evidence row, $\LocatedRealUp$ comparison row, $\TopologyUp$ consumer row, $\StreamNameUp$ schedule, $\RegSeqRatUp$ readback, open-neighbourhood ledger, transport, replay, provenance, and local naming;
\item apartness-positive visibility, requiring the positive radius, endpoint readbacks, and separation ledger to be displayed in $A$ before any neighbourhood is generated;
\item located comparison visibility, requiring every comparison used by the neighbourhood request to pass through the located row $L$ and the shared $W,Q$ windows;
\item topology admission, requiring the topology-facing consumer to read only the generated ledger $O$ through $T$;
\item structural stability, requiring $H,C,P,N$ to transport, replay, source, and name only the rows already listed.
\end{enumerate}
No Bishop real apartness topology obligation is stored outside $B$, and the packet exports no trichotomy, host open set, quotient real equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-real-apartness-topology-carrier}. The displayed packet exposes exactly the real name, apartness-positive evidence, located comparison row, topology consumer row, stream schedule, regular readback, open-neighbourhood ledger, and structural rows.

Apartness-positive visibility is the row $A$. It carries the positive radius, endpoint readbacks, and separation ledger before the open-neighbourhood ledger is generated, so no trichotomy or host inequality row is needed.

Located comparison visibility is the row $L$ together with $W$ and $Q$. These rows align the comparison request with the finite stream window and regular-rational readback used by the same real name.

Topology admission is forced through $O$ and $T$. The ledger $O$ is generated only after the apartness and located rows have been displayed, and $T$ admits that ledger as the topology-facing surface.

Finally $H,C,P,N$ preserve only the displayed rows by transport, replay, provenance, and local naming. Since the carrier has no coordinate for host open sets, quotient equality, choice, completeness, or detached topology data, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bishop real apartness topology Real seal]
\label{thm:bishop-real-apartness-topology-real-seal}
Every $\RealUp$-facing or $\TopologyUp$-facing consumer of an accepted $\BishopRealApartnessTopologyUp$ carrier must pass through the route
$$
R,A,L,W,Q,O,H,C,P,N
$$
before reading the topology row $T$. The handoff exposes the real name, apartness-positive evidence, located comparison rows, finite stream schedule, regular rational readback, open-neighbourhood ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row, but it exports no trichotomy, host open set, quotient real equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a Real-facing or topology-facing read of the accepted carrier. The only real-name source is $R$, and its finite observations are read through $W$ and $Q$.

The neighbourhood evidence is forced through $A$ and $L$. The apartness-positive row supplies the displayed separation ledger, while the located comparison row supplies the comparison windows used by the same request.

The topology consumer can read only after $O$ has been generated. Thus $T$ receives a ledger assembled from the displayed real, apartness, locatedness, stream, and regular-readback rows, not a host open set or quotient-open representative.

The structural rows $H,C,P,N$ transport, replay, source, and name that same route. Since the carrier contains no trichotomy, quotient equality, countable-choice, host-open, or completeness coordinate, every accepted handoff remains on the displayed finite route.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopRealApartnessTopologyUp$ Real-facing or topology-facing read factors through $\RealUp$, $\ApartnessRealUp$, $\LocatedRealUp$, $\TopologyUp$, $\StreamNameUp$, $\RegSeqRatUp$, open-neighbourhood ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows.}

\independenceWitness{real, apartnessreal, locatedreal, topology, streamname, regseqrat: $\BishopRealApartnessTopologyUp$ is not bijective to any listed sibling because it jointly carries a real-name seal, apartness-positive evidence, located comparison rows, a topology-facing neighbourhood ledger, finite stream windows, regular rational readback, transport, replay, provenance, and local naming as one constructive topology packet.}

\closureat{BishopRealApartnessTopologyUp}{seedStr}

\begin{closurestatus}{\BishopRealApartnessTopologyUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-real-apartness-topology-carrier}, \autoref{thm:bishop-real-apartness-topology-namecert-obligations}, and \autoref{thm:bishop-real-apartness-topology-real-seal} seed the finite Bishop real apartness topology route through $\RealUp$, $\ApartnessRealUp$, $\LocatedRealUp$, $\TopologyUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close trichotomy, host open sets, quotient real equality, countable choice, Lean theorem checking, bridge checking, or ambient completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, apartness-positive visibility, located comparison visibility, topology admission, Real seal handoff, transport stability, and replay stability for BEDC.Derived.BishopRealApartnessTopologyUp.}
  \constructivestory{The construction starts from a Bishop real name, records apartness-positive and located comparison evidence over finite StreamName and RegSeqRat windows, generates an open-neighbourhood ledger, and exposes the topology-facing consumer only along the same finite NameCert route.}
\end{closurestatus}
