\chapter{A Concrete Naming Certificate for $\MaschkeTheoremUp$}
\label{ch:concrete-instances-maschke-theorem-namecert}
\origin{human}

Following Maschke's theorem for finite-group representations, the $\MaschkeTheoremUp$ packet records a finite averaging-projector and complement-decomposition ledger. It reads the group source of \autoref{ch:concrete-instances-group-namecert}, the vector-space source of \autoref{ch:concrete-instances-vecspace-namecert}, the character-theory and representation-ring rows of \autoref{ch:concrete-instances-charactertheory-namecert} and \autoref{ch:concrete-instances-representationring-namecert}, and the orthogonality surface of \autoref{ch:concrete-instances-schurorthogonality-namecert}. The packet names only the displayed finite semisimplicity route; it is not a host representation category, not a quotient-subrepresentation construction, and not a global semisimplicity theorem.

\begin{definition}[Maschke theorem carrier]
\label{def:maschke-theorem-carrier}
A $\MaschkeTheoremUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
K=(G,V,R,X,A,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the finite $\GroupUp$ source row supplying the group operation, unit, inverse, and finite averaging support;
\item $V$ is the $\VecSpaceUp$ source row supplying the represented vector carrier and its addition, scalar, and zero rows;
\item $R$ is the $\RepresentationRingUp$ row recording the representation input and the direct-sum handoff surface;
\item $X$ is the invariant-subspace row, displayed as a carried subobject of the represented vector row rather than as a quotient representation;
\item $A$ is the averaging-projector row, storing the finite group average used to make a raw complement map invariant;
\item $Q$ is the complement row, recording the kernel-image decomposition exposed by the averaged projector;
\item $H$ is the componentwise $\hsame$ transport for $G,V,R,X,A,Q$;
\item $C$ is the $\Cont$ replay row for the averaging and complement ledgers;
\item $P$ is the $\Pkg$ provenance over $\GroupUp$, $\VecSpaceUp$, $\CharacterTheoryUp$, $\RepresentationRingUp$, $\SchurOrthogonalityUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\MaschkeTheoremUp}$ evidence.
\end{enumerate}
The carrier has no coordinate for a host representation category, a quotient subrepresentation carrier, a selected basis, or a global semisimplicity theorem outside the displayed rows.
\end{definition}

\begin{theorem}[Maschke theorem NameCert obligations]
\label{thm:maschke-theorem-namecert-obligations}
The local $\NameCert_{\MaschkeTheoremUp}$ surface for the carrier of \autoref{def:maschke-theorem-carrier} consists of the finite obligations that admit the group source $G$, the vector source $V$, the representation row $R$, the invariant-subspace row $X$, the averaging projector $A$, the complement row $Q$, and the transport, replay, provenance, and local naming rows $H,C,P,N$. These obligations export no host representation category, quotient subrepresentation carrier, selected basis, or global semisimplicity theorem outside $G,V,R,X,A,Q,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier rows of \autoref{def:maschke-theorem-carrier}. The group row is read through \autoref{ch:concrete-instances-group-namecert}, while the vector row is read through \autoref{ch:concrete-instances-vecspace-namecert}.

Next read the representation surface through \autoref{ch:concrete-instances-representationring-namecert} and the character-theory support through \autoref{ch:concrete-instances-charactertheory-namecert}. These rows account for $R$ and for the finite representation-theoretic evidence consumed by the averaging ledger.

Finally inspect the remaining rows. The invariant subspace $X$, averaging projector $A$, and complement row $Q$ are preserved only by the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows $H,C,P,N$. Since the carrier contains no further coordinate, the excluded host category, quotient carrier, basis selection, and global semisimplicity data cannot be exported.
\end{proof}

\begin{theorem}[Maschke averaging-projector route]
\label{thm:maschke-theorem-averaging-projector-route}
Every complement-facing consumer of an accepted $\MaschkeTheoremUp$ packet must pass through
$$
G \longmapsto V \longmapsto R \longmapsto X \longmapsto A \longmapsto Q \longmapsto H,C,P,N .
$$
The averaging row $A$ is read as a finite $\GroupUp$ average over the represented $\VecSpaceUp$ row and the representation row $R$, and the complement row $Q$ is read only after that projector row has been displayed. The route exports no host representation category, quotient subrepresentation carrier, selected basis, or global semisimplicity theorem.
\end{theorem}
\begin{proof}
Begin with the group and vector sources. The finite averaging support is supplied by \autoref{ch:concrete-instances-group-namecert}, and the linear target of the average is supplied by \autoref{ch:concrete-instances-vecspace-namecert}.

Then use the representation rows. The representation-ring certificate of \autoref{ch:concrete-instances-representationring-namecert} identifies the action row $R$, while the character-theory and Schur-orthogonality surfaces of \autoref{ch:concrete-instances-charactertheory-namecert} and \autoref{ch:concrete-instances-schurorthogonality-namecert} supply the finite representation-theoretic ledger read by the projector route.

The complement row is downstream of the averaging row. Once $A$ is displayed, $Q$ records only the finite complement decomposition and the rows $H,C,P,N$ replay and name that route. No listed sibling chapter supplies a hidden host category, quotient subrepresentation carrier, selected basis, or global semisimplicity theorem, so the consumer cannot receive those objects from this packet.
\end{proof}

\begin{theorem}[Maschke representation-ring handoff]
\label{thm:maschke-theorem-representation-ring-handoff}
Every $\RepresentationRingUp$-facing read of an accepted $\MaschkeTheoremUp$ packet receives only the finite handoff from the group and vector rows to the representation row $R$, the invariant row $X$, the averaging row $A$, the complement row $Q$, and the structural rows $H,C,P,N$. The handoff may record a displayed direct-sum decomposition row, but it does not create a host representation category, quotient subrepresentation carrier, selected basis, or global semisimplicity theorem outside the finite packet.
\end{theorem}
\begin{proof}
First expose the representation-ring dependency. The handoff begins at \autoref{ch:concrete-instances-representationring-namecert}, whose rows name representation addition and direct-sum bookkeeping over the underlying group and vector surfaces.

Next attach the finite Maschke rows. The invariant row $X$ and the averaging projector row $A$ produce the complement row $Q$ only through the displayed packet route, with \autoref{ch:concrete-instances-schurorthogonality-namecert} available as a finite orthogonality-side ledger rather than as a basis selector.

Finally repack the handoff through $H,C,P,N$. These rows transport, replay, source, and name the same finite route for $\RepresentationRingUp$ consumers. Since no quotient carrier, host category, selected basis, or global semisimplicity coordinate is present, the handoff remains confined to the displayed rows.
\end{proof}

\closureat{MaschkeTheoremUp}{seedStr}

\begin{closurestatus}{\MaschkeTheoremUp}
  \constructivestory{A $\MaschkeTheoremUp$ packet is generated from a finite $\GroupUp$ source row, a $\VecSpaceUp$ source row, a $\RepresentationRingUp$ row, an invariant-subspace row, an averaging-projector row, a complement row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:maschke-theorem-carrier}, \autoref{thm:maschke-theorem-namecert-obligations}, \autoref{thm:maschke-theorem-averaging-projector-route}, and \autoref{thm:maschke-theorem-representation-ring-handoff} seed the finite averaging-projector and complement-decomposition route for finite-group representation consumers.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.MaschkeTheoremUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host representation category, quotient subrepresentation carrier, selected basis, or global semisimplicity theorem.}
  \upgradepath{Obligation closure requires checked group, vector, representation-ring, invariant-subspace, averaging-projector, complement, transport, replay, provenance, and local naming rows for the displayed packet.}
\end{closurestatus}
