\chapter{A Concrete Naming Certificate for $\NestedCauchyRealSectionUp$}
\label{ch:concrete-instances-nested-cauchy-real-section-namecert}
\origin{human}

Bishop--Bridges constructive analysis treats nested Cauchy sections as finite approximation data before any completed real object is read. The $\NestedCauchyRealSectionUp$ packet names that Real and Completion phase surface over the nested-interval carrier of \autoref{ch:concrete-instances-nestedinterval-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. It packages nested Cauchy section data for downstream completion consumers without asserting completeness of $\RealUp$.

\begin{definition}[Nested Cauchy real section carrier]
\label{def:nested-cauchy-real-section-carrier}
A $\NestedCauchyRealSectionUp$ carrier is a finite $\BHist$ packet
$$
S=(I,T,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the nested interval row, containing the finite interval chain, endpoint order data, and the diameter bounds consumed from \autoref{ch:concrete-instances-nestedinterval-namecert}.
\item $T$ is the cofinal tail-window row, assigning each requested tolerance a finite interval index and the later windows through which the section may be inspected.
\item $W$ is the $\StreamNameUp$ observation row, exposing only finite stream windows before any regular rational readback is available.
\item $R$ is the $\RegSeqRatUp$ row reached from the stream windows and the nested interval endpoints.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic comparison budgets for endpoint width, tail inclusion, and section readback.
\item $E$ is the terminal $\RealUp$ seal row exposed only after $I,T,W,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for nested intervals, tail windows, stream observations, regular readback, dyadic tolerance ledgers, Real seals, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a Real or Completion request through $T,D,W,R,I$ and then into the displayed $\RealUp$ seal.
\item $P$ is the $\Pkg$ provenance over $\NestedCauchyRealSectionUp$, $\NestedIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedCauchyRealSectionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,T,W,R,D,E,H,C,P,N$. The carrier has no coordinate for quotient stream equality, selected limits, countable choice, host real equality, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Nested Cauchy real section NameCert obligations]
\label{thm:nested-cauchy-real-section-namecert-obligations}
For every accepted $\NestedCauchyRealSectionUp$ carrier $S=(I,T,W,R,D,E,H,C,P,N)$, the local $\NameCert_{\NestedCauchyRealSectionUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the nested interval row, cofinal tail windows, finite stream observations, regular rational readback, dyadic tolerance ledger, Real seal, transport, replay, provenance, and local naming rows;
\item tail-window exactness, requiring every Real or Completion tolerance request to expose $T$ before reading $W,R,D$;
\item nested-interval compatibility, requiring the interval chain $I$ and dyadic ledger $D$ to control endpoint width, tail inclusion, and section readback;
\item Real-seal handoff, requiring the terminal $\RealUp$ row $E$ to be read only after $I,T,W,R,D$ have been displayed;
\item ledger non-escape, requiring $H,C,P,N$ to transport, replay, source, and name only the displayed packet and to export no quotient stream, selected limit, countable choice, host real equality, or ambient Real completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:nested-cauchy-real-section-carrier}. The tuple displays the nested intervals, tail windows, stream windows, regular readback, dyadic ledger, Real seal, and structural rows.

Tail-window exactness follows from the placement of $T$. A tolerance request reaches finite observations and regular readback only through the displayed cofinal window, so no off-packet schedule can be used.

Nested-interval compatibility is the joint route through $I$ and $D$. The interval chain supplies the nested endpoint data, while the dyadic ledger supplies the width and comparison budgets.

The Real seal is downstream of those rows. The replay row $C$ reaches $E$ only after $I,T,W,R,D$ are visible, and $H,P,N$ preserve and name that same route.

The excluded objects are absent from the carrier. Hence quotient streams, selected limits, countable choice, host real equality, and ambient Real completeness cannot appear as local NameCert obligations.
\end{proof}

\begin{theorem}[Nested Cauchy real section Real-completion handoff]
\label{thm:nested-cauchy-real-section-real-completion-handoff}
Every completion-facing read of an accepted $\NestedCauchyRealSectionUp$ carrier factors through the $\NestedIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows before it exposes the local section certificate. The handoff exports finite interval, tolerance, observation, regular-readback, and Real-seal data, and exports no quotient stream, selected limit, countable choice, host real equality, or ambient Real completeness theorem.
\end{theorem}
\begin{proof}
Start from an accepted packet $S=(I,T,W,R,D,E,H,C,P,N)$. Projection gives the nested interval row $I$, cofinal tail row $T$, finite stream observations $W$, regular rational readback $R$, dyadic tolerance ledger $D$, terminal Real seal $E$, and structural rows.

A completion-facing tolerance request is replayed through $C$. The replay fixes the tail window $T$, reads dyadic budgets from $D$, opens the stream window $W$, obtains regular rational readback from $R$, and checks the nested interval row $I$ before exposing the Real seal $E$.

The structural rows add no external completion principle. They transport, replay, source, and name the same finite rows, so the read cannot export a quotient stream, a selected limit, countable choice, host real equality, or ambient completeness of $\RealUp$.
\end{proof}

\begin{theorem}[Nested Cauchy real section choice-free Real seal]
\label{thm:real-regular-cauchy-seal-choice-free}
Every accepted $\NestedCauchyRealSectionUp$ packet exposes its terminal $\RealUp$ seal only through the displayed nested interval, cofinal tail-window row, finite $\StreamNameUp$ observation row, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ tolerance rows. The exported Real-facing boundary contains no quotient stream, selected limit, countable-choice row, host real equality, or ambient Real-completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier tuple $S=(I,T,W,R,D,E,H,C,P,N)$ of \autoref{def:nested-cauchy-real-section-carrier}. The terminal Real seal is the row $E$, and the rows available before it are exactly the nested interval row $I$, cofinal tail-window row $T$, finite observation row $W$, regular rational readback row $R$, and dyadic tolerance ledger $D$.

Apply the Real-completion handoff theorem. It forces every completion-facing read to pass through $I,T,W,R,D$ before exposing the local section certificate and the terminal Real seal.

The refused objects are absent from the carrier definition. Since no coordinate names a quotient stream, selected limit, countable-choice row, host real equality, or ambient Real-completeness theorem, the seal exported by $E$ is choice-free in exactly the displayed packet sense.
\end{proof}

\closureat{NestedCauchyRealSectionUp}{seedStr}

\begin{closurestatus}{\NestedCauchyRealSectionUp}
  \constructivestory{A $\NestedCauchyRealSectionUp$ packet is generated from nested interval rows, cofinal tail windows, finite $\StreamNameUp$ observations, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledgers, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-cauchy-real-section-carrier}, \autoref{thm:nested-cauchy-real-section-namecert-obligations}, and \autoref{thm:nested-cauchy-real-section-real-completion-handoff} seed the finite nested Cauchy section handoff surface for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient streams, selected limits, countable choice, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tail-window exactness, nested-interval compatibility, dyadic tolerance stability, regular rational readback, Real-seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.NestedCauchyRealSectionUp.}
\end{closurestatus}
