\chapter{A Concrete Naming Certificate for $\LawCertificateUp$}
\label{ch:concrete-instances-law-certificate-namecert}
\origin{ai}

The $\LawCertificateUp$ packet realizes the law-certificate discipline of \autoref{sec:physical-induction-open-continuation} as a finite NameCert surface. It sits after the physical-induction carrier of \autoref{ch:concrete-instances-reality-constrained-physical-induction-namecert}, the open-fit packet of \autoref{ch:concrete-instances-open-fit-packet-namecert}, the model-audit packet of \autoref{ch:concrete-instances-reality-constrained-model-audit-namecert}, the induction-stability seal of \autoref{ch:concrete-instances-physical-induction-stability-seal-namecert}, and the tower-compression packet of \autoref{ch:concrete-instances-reality-constrained-tower-compression-namecert}. Those siblings supply finite fit, audit comparison, continuation stability, and compression-residue surfaces; this packet binds an equation-like pattern to source fit, classifier, stability, failure surface, ledger, transport, provenance, and local naming before any consumer may read it as a physical law.

\begin{definition}[Law certificate carrier]
\label{def:law-certificate-carrier}
A $\LawCertificateUp$ carrier is a finite $\BHist$ packet
$$
L=(F,P,C,S,E,Ld,H,R,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite source-fit row, read through $\OpenFitPacketUp$ and $\RealityConstrainedPhysicalInductionUp$, recording the observations that license the equation-like pattern.
\item $P$ is the pattern row naming the equation, invariant, or calculation rule being offered as lawlike.
\item $C$ is the classifier row comparing model-generated and source-observed signatures under the admitted observational equivalence.
\item $S$ is the continuation-stability row, read through $\PhysicalInductionStabilitySealUp$, naming the continuation class and stability basis under which reuse is licensed.
\item $E$ is the explicit failure-surface row naming observations, refined histories, or tower-level reads that would defeat the law claim.
\item $Ld$ is the ledger row recording idealizations, hidden assumptions, tower-compression residue, audit strength, and refused final-fit demands.
\item $H$ records componentwise $\hsame$ transport for $F,P,C,S,E,Ld,R,Q,N$.
\item $R$ records displayed $\Cont$ replay through source fit, pattern use, classifier comparison, stability reuse, failure exposure, and ledger inspection.
\item $Q$ is the $\Pkg$ provenance over $\LawCertificateUp$, $\OpenFitPacketUp$, $\RealityConstrainedPhysicalInductionUp$, $\RealityConstrainedModelAuditUp$, $\PhysicalInductionStabilitySealUp$, $\RealityConstrainedTowerCompressionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\LawCertificateUp}$ row.
\end{enumerate}
The carrier has no coordinate for a bare equation, unbounded natural law, final-fit oracle, detached model syntax, hidden stability assumption, omitted failure surface, or ledger-free physical truth. A physical law is public only as the displayed packet $L$.
\end{definition}
\leandef{BEDC.Derived.LawCertificateUp.LawCertificateUp}

\begin{definition}[Law certificate classifier]
\label{def:law-certificate-classifier}
The $\LawCertificateUp$ classifier identifies two accepted packets only when their source-fit rows, equation-pattern rows, classifier rows, continuation-stability rows, failure-surface rows, ledger rows, transport rows, replay rows, provenance rows, and local NameCert rows agree through displayed componentwise $\hsame$ transport. Agreement of the equation-like pattern alone is not enough, and finite source fit without stability or failure exposure is not enough.
\end{definition}

\begin{theorem}[Law certificate NameCert obligations]
\label{thm:law-certificate-namecert-obligations}
For the carrier of \autoref{def:law-certificate-carrier}, the local $\NameCert_{\LawCertificateUp}$ surface consists exactly of seven finite obligations:
\begin{enumerate}
\item carrier admission for $L=(F,P,C,S,E,Ld,H,R,Q,N)$;
\item source-fit exposure through $F$;
\item equation-pattern exposure through $P$ without treating the pattern as self-licensing;
\item classifier exposure through $C$;
\item continuation-stability and failure-surface exposure through $S$ and $E$;
\item ledger accountability through $Ld$, including audit strength, compression residue, idealization, and refused final-fit demands;
\item transport, replay, provenance, and local naming through $H,R,Q,N$.
\end{enumerate}
These seven rows are the complete public obligation surface for reading an equation-like pattern as a physical law.
\end{theorem}
\leanchecked{BEDC.Derived.LawCertificateUp.LawCertificate\_semantic\_name\_certificate}
\begin{proof}
Carrier admission is projection from \autoref{def:law-certificate-carrier}. The packet exposes source fit, pattern, classifier, continuation stability, failure surface, ledger, transport, replay, provenance, and local name as its complete finite surface.

Source-fit exposure comes from $F$, while pattern exposure comes from $P$. The classifier row $C$ states how the model-generated signatures and source-observed signatures are compared; therefore the pattern is not read in isolation from the source and classifier data that make it empirical.

Continuation stability and failure exposure are supplied by $S$ and $E$. The ledger row $Ld$ records the audit, tower, idealization, and refusal data that prevent the packet from becoming an unbounded natural-law oracle.

Finally $H,R,Q,N$ preserve and name the same displayed packet. Since the carrier has no further coordinate for hidden stability, detached model syntax, or ledger-free truth, the seven listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Law certificate failure-surface nonescape]
\label{thm:law-certificate-failure-surface-nonescape}
An accepted $\LawCertificateUp$ packet cannot be reduced to an equation pattern plus finite fit while preserving law status. Any public read that drops either the continuation-stability row $S$ or the failure-surface row $E$ leaves the accepted classifier surface.
\end{theorem}
\leanchecked{BEDC.Derived.LawCertificateUp.lawCertificate\_failure\_surface\_rows\_nonescape}
\begin{proof}
Project the carrier as $L=(F,P,C,S,E,Ld,H,R,Q,N)$. The rows $F$ and $P$ record finite source fit and the equation-like pattern, but they do not state which continuations are licensed or what observations would defeat the law claim.

Apply the classifier of \autoref{def:law-certificate-classifier}. It compares accepted packets through $S$ and $E$ together with $F,P,C,Ld,H,R,Q,N$. Dropping either $S$ or $E$ therefore changes the public comparison surface.

Transport, replay, provenance, and local naming preserve only the displayed rows. Because the carrier has no hidden coordinate for stability or failure exposure, no off-packet route can recover law status from equation syntax and finite fit alone.
\end{proof}

\begin{theorem}[Law certificate continuation scope]
\label{thm:law-certificate-continuation-scope}
Every accepted $\LawCertificateUp$ consumer read of a physical law is scoped to the continuation-stability row $S$, the failure-surface row $E$, and the ledger row $Ld$. The packet licenses prediction only inside that displayed scope and does not assert total future fit.
\end{theorem}
\begin{proof}
The NameCert obligations of \autoref{thm:law-certificate-namecert-obligations} require $S,E,Ld$ before the local name is accepted. These rows state the continuation class, the defeating observations, and the audit-and-residue ledger that bound reuse.

The nonescape result of \autoref{thm:law-certificate-failure-surface-nonescape} rules out reading law status after removing either continuation stability or failure exposure. The ledger row also remains visible, so idealization residue and tower-compression assumptions are part of the same public packet.

Thus the consumer-visible law is not a total claim over all possible observation histories. It is a certificate-relative read whose scope is exactly the displayed source fit, classifier, stability, failure surface, ledger, transport, provenance, and local NameCert rows.
\end{proof}

The Lean follow-up file \texttt{lean4/BEDC/Derived/LawCertificateUp/TasteGate.lean} must provide explicit $\Nontrivial\ \LawCertificateUp$ and $\FieldFaithful\ \LawCertificateUp$ instances, with witness-pair and field-projection proofs preserving $F,P,C,S,E,Ld,H,R,Q,N$ as separate displayed fields.

\falsifiablePrediction{A packet that presents an equation and finite fit but omits either the continuation-stability row or the failure-surface row is rejected by the LawCertificateUp classifier.}

\independenceWitness{realityconstrainedphysicalinduction, openfitpacket, realityconstrainedmodelaudit, physicalinductionstabilityseal, realityconstrainedtowercompression: none is bijective because LawCertificateUp binds equation pattern, source fit, classifier, continuation stability, failure surface, ledger, transport, provenance, and local NameCert rows in one carrier, while each sibling supplies only a constituent surface.}

\closureat{LawCertificateUp}{seedStr}

\begin{closurestatus}{\LawCertificateUp}
  \constructivestory{A $\LawCertificateUp$ packet is generated from finite source-fit, equation-pattern, classifier, continuation-stability, failure-surface, ledger, componentwise hsame, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:law-certificate-carrier}, \autoref{def:law-certificate-classifier}, \autoref{thm:law-certificate-namecert-obligations}, \autoref{thm:law-certificate-failure-surface-nonescape}, and \autoref{thm:law-certificate-continuation-scope} bind the finite law-certificate carrier, classifier, obligation surface, failure-surface boundary, and continuation scope.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, total physical law, all-history prediction, equation-only law status, hidden stability, or ledger-free physical truth.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier exposure, continuation-stability exposure, failure-surface nonescape, continuation-scope preservation, TasteGate nontriviality, and field faithfulness for $F,P,C,S,E,Ld,H,R,Q,N$.}
\end{closurestatus}
