\chapter{A Concrete Naming Certificate for $\WindowCoverageTriggerAlgebraUp$}
\label{ch:concrete-instances-window-coverage-trigger-algebra-namecert}
\origin{ai}

The $\WindowCoverageTriggerAlgebraUp$ packet realizes the finite support-closure algebra of \autoref{def:philosophy-coverage-trigger-system} and \autoref{thm:philosophy-universal-coverage-trigger-algebra-theorem} as BEDC NameCert data. It consumes the boundary-tile row of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the coverage-rank row of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the finite observation interface of \autoref{ch:concrete-instances-finite-observation-interface-namecert}, the observer support lattice of \autoref{ch:concrete-instances-observer-support-lattice-namecert}, and the finite residue boundary of \autoref{ch:concrete-instances-finite-observation-residue-boundary-namecert}. The packet names closure of visible trigger supports under finite windows; it is not a hidden global semantics, stochastic evolution model, quotient codon space, or infinite coverage oracle.

\begin{definition}[Window coverage-trigger algebra carrier]
\label{def:window-coverage-trigger-algebra-carrier}
A $\WindowCoverageTriggerAlgebraUp$ carrier is a finite $\BHist$ packet
$$
W=(T,C,F,L,R,A,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\DnaWindowSixBoundaryTileUp$ trigger-boundary row exposing the finite window classifiers whose supports are read.
\item $C$ is the $\SixBoundaryTileCoverageUp$ coverage row, recording which visible triggers cover which displayed support faces.
\item $F$ is the $\FiniteObservationInterfaceUp$ row that bounds every trigger read by a selected finite window and an omitted-tail ledger.
\item $L$ is the $\ObserverSupportLatticeUp$ support-lattice row, used only as a finite inclusion and coverage-rank ledger.
\item $R$ is the $\FiniteObservationResidueBoundaryUp$ residue row, recording which support faces remain outside the current closure.
\item $A$ is the trigger-algebra row, carrying the finite support set, closure set, blocker row, coverage threshold row, and handoff to the $(4,2)$ codon instance when that instance is requested.
\item $H$ records componentwise $\hsame$ transport for the trigger-boundary, coverage, finite-window, support-lattice, residue, algebra, replay, provenance, and naming rows.
\item $Q$ records displayed $\Cont$ replay from a coverage-trigger request through $T,C,F,L,R,A$.
\item $P$ is the $\Pkg$ provenance over $\WindowCoverageTriggerAlgebraUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\FiniteObservationInterfaceUp$, $\ObserverSupportLatticeUp$, $\FiniteObservationResidueBoundaryUp$, the source vision of \autoref{def:philosophy-coverage-trigger-system}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\WindowCoverageTriggerAlgebraUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,C,F,L,R,A,H,Q,P,N$. It has no coordinate for hidden biological semantics, stochastic transition laws, quotient codon equality, global support completion, infinite search over triggers, or a final coverage oracle.
\end{definition}

\begin{theorem}[Window coverage-trigger algebra NameCert obligations]
\label{thm:window-coverage-trigger-algebra-namecert-obligations}
For every accepted $\WindowCoverageTriggerAlgebraUp$ carrier $W=(T,C,F,L,R,A,H,Q,P,N)$, the local $\NameCert_{\WindowCoverageTriggerAlgebraUp}$ surface consists exactly of boundary-trigger admission through $T$, coverage-rank admission through $C$, finite-window exposure through $F$, support-lattice inclusion through $L$, residue-boundary accounting through $R$, algebra-row exactness through $A$, componentwise transport through $H$, displayed replay through $Q$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:window-coverage-trigger-algebra-carrier}. The accepted packet exposes only the boundary trigger, coverage, finite-window, support-lattice, residue, trigger-algebra, transport, replay, provenance, and naming rows.

The trigger read starts with $T,C,F$. A consumer first sees the displayed boundary-tile classifiers, then the coverage-rank row, and then the finite observation interface that records the selected window and omitted-tail ledger.

The support and residue stages are $L,R$. The support lattice provides finite inclusion and coverage-rank comparison, while the residue row records which faces remain outside the displayed closure.

The algebra row $A$ may then package the support set, closure set, blocker row, threshold row, and $(4,2)$ handoff. The structural rows $H,Q,P,N$ preserve only this displayed route, so hidden semantics, stochastic laws, quotient codon equality, global support completion, infinite trigger search, and final coverage oracles have no carrier coordinate.
\end{proof}

\begin{theorem}[Window coverage-trigger vision handoff]
\label{thm:window-coverage-trigger-algebra-vision-handoff}
Every concrete read of the universal coverage-trigger system through $\WindowCoverageTriggerAlgebraUp$ factors through the finite route
$$
\DnaWindowSixBoundaryTileUp \longrightarrow \SixBoundaryTileCoverageUp \longrightarrow \FiniteObservationInterfaceUp \longrightarrow \ObserverSupportLatticeUp \longrightarrow \FiniteObservationResidueBoundaryUp .
$$
The exported object is the finite support-closure trigger algebra carried by $T,C,F,L,R,A,H,Q,P,N$, with the source vision used only as provenance for the displayed closure, blocker, threshold, and codon-instance rows.
\end{theorem}
\begin{proof}
Start with the coverage-trigger definitions in \autoref{def:philosophy-coverage-trigger-system}. The concrete packet does not import the whole vision as an oracle; it reads only the finite trigger-boundary and coverage rows $T,C$.

Next bind finite access through $F$. The selected window and omitted-tail ledger determine which trigger supports are visible before any closure row can be exported.

Then read $L$ and $R$. The support lattice records finite inclusion and coverage rank, while the residue boundary records the uncovered faces that remain outside the current closure.

Finally package the closure, blocker, threshold, and codon-instance handoff through $A,H,Q,P,N$. Since these rows preserve the displayed finite route, every concrete read of the universal coverage-trigger algebra factors through the NameCert packet rather than through hidden semantics, quotient codon equality, stochastic dynamics, or infinite trigger search.
\end{proof}

\begin{theorem}[Window coverage-trigger algebra Markov source route]
\label{thm:window-coverage-trigger-algebra-markov-source-route}
Every Markov-trigger-facing consumer of $\WindowCoverageTriggerAlgebraUp$ must read the boundary-trigger row of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the coverage-rank row of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the finite-observation window row of \autoref{ch:concrete-instances-finite-observation-interface-namecert}, the support-lattice row of \autoref{ch:concrete-instances-observer-support-lattice-namecert}, and the residue-boundary row of \autoref{ch:concrete-instances-finite-observation-residue-boundary-namecert} before any Markov state transition row can be formed.

Thus the rank-sensitive transition surface of \autoref{thm:philosophy-rank-markov-transition} is reached only after the finite support-closure route $T,C,F,L,R,A,H,Q,P,N$ has exposed boundary triggers, coverage rank, finite windows, support inclusion, and residue accounting. The route exports no stochastic evolution law, hidden biological semantics, quotient codon equality, global support completion, or infinite trigger search.
\end{theorem}
\begin{proof}
Start with a consumer that requests a Markov-trigger-facing transition row. The carrier of \autoref{def:window-coverage-trigger-algebra-carrier} exposes no transition coordinate before the boundary-trigger, coverage, finite-window, support-lattice, and residue rows have been read.

The source route is therefore $T,C,F,L,R$. These rows are supplied by the five sibling concrete chapters named in the statement and fix the displayed boundary triggers, rank data, finite observation window, support inclusion, and residue boundary before any transition-facing handoff is admissible.

Only after that route is displayed may $A,H,Q,P,N$ package the trigger algebra for the rank-sensitive surface of \autoref{thm:philosophy-rank-markov-transition}. Since the carrier contains no stochastic evolution row, hidden biological semantics, quotient codon equality, global support completion, or infinite trigger-search coordinate, none of those objects can be introduced by the Markov source route.
\end{proof}

\falsifiablePrediction{Every accepted $\WindowCoverageTriggerAlgebraUp$ consumer that claims coverage-trigger closure must exhibit the boundary-trigger row, coverage-rank row, finite-observation row, support-lattice row, residue-boundary row, algebra row, componentwise transport, replay, provenance, and local naming row. A consumer omitting any of probe-bundle, finite-observation, support-lattice, namecert, or trigger-boundary sibling slugs refutes the packet.}

\independenceWitness{probe-bundle, finite-observation, support-lattice, namecert, trigger-boundary, six-boundary-tile-coverage: $\WindowCoverageTriggerAlgebraUp$ is not bijective to any listed sibling because it jointly carries boundary triggers, coverage rank, finite-window access, support closure, residue accounting, algebraic blocker and threshold rows, transport, replay, provenance, and local naming.}

The later Lean route for \texttt{BEDC.Derived.WindowCoverageTriggerAlgebraUp} must provide explicit $\Nontrivial\ \WindowCoverageTriggerAlgebraUp$ and $\FieldFaithful\ \WindowCoverageTriggerAlgebraUp$ instances preserving $T,C,F,L,R,A,H,Q,P,N$ as separate displayed fields.

\closureat{WindowCoverageTriggerAlgebraUp}{seedStr}

\begin{closurestatus}{\WindowCoverageTriggerAlgebraUp}
  \constructivestory{A $\WindowCoverageTriggerAlgebraUp$ packet is generated from boundary-trigger rows, coverage-rank rows, finite observation windows, support-lattice inclusion rows, residue-boundary rows, a trigger-algebra row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:window-coverage-trigger-algebra-carrier}, \autoref{thm:window-coverage-trigger-algebra-namecert-obligations}, and \autoref{thm:window-coverage-trigger-algebra-vision-handoff} seed the finite support-closure trigger algebra over boundary tiles, coverage rows, finite observation windows, support lattices, residue boundaries, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close hidden biological semantics, stochastic transition laws, quotient codon equality, global support completion, infinite trigger search, final coverage oracles, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, boundary-trigger exactness, coverage-rank exactness, finite-window non-escape, support-lattice inclusion, residue accounting, Nontrivial WindowCoverageTriggerAlgebraUp, and FieldFaithful WindowCoverageTriggerAlgebraUp for BEDC.Derived.WindowCoverageTriggerAlgebraUp.}
\end{closurestatus}
