\chapter{A Concrete Naming Certificate for $\HyperbolicGeodesicBoundaryUp$}
\label{ch:concrete-instances-hyperbolic-geodesic-boundary-namecert}
\origin{ai}

The $\HyperbolicGeodesicBoundaryUp$ packet realizes the boundary-geodesic route of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite Poincare-disk, hyperbolic-metric, phase-transport, and provenance rows. It sits after the disk-coordinate surface of \autoref{ch:concrete-instances-unitdisk-namecert}, reversible transport in \autoref{ch:concrete-instances-unitarygroup-namecert}, finite flow rows in \autoref{ch:concrete-instances-dynsystem-namecert}, the disk-phase carrier of \autoref{ch:concrete-instances-poincare-disk-phase-transport-namecert}, and the metric-read surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}. The packet names geodesic-boundary data without treating the boundary as a completed host circle, quotient ideal point, physical horizon, or observer substance.

\begin{definition}[HyperbolicGeodesicBoundary carrier]
\label{def:hyperbolic-geodesic-boundary-carrier}
A $\HyperbolicGeodesicBoundaryUp$ carrier is a finite $\BHist$ packet
$$
G=(D,M,T,B,J,F,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ disk-coordinate row, including the finite radius and boundary-approach observations used by the packet.
\item $M$ is the $\HyperbolicMetricUp$ metric-read row over the same displayed disk data.
\item $T$ is the $\PoincareDiskPhaseTransportUp$ transport row, retaining reversible phase movement, finite flow data, and fiber provenance.
\item $B$ is the boundary-geodesic incidence row, recording which finite disk observations are read as approaching the same geodesic far-end.
\item $J$ is the classifier-stability row, preserving disk-coordinate, hyperbolic-metric, phase-transport, and boundary-geodesic classifiers under the displayed route.
\item $F$ is the refusal row excluding quotient boundary equality, completed geodesic compactification, host horocycle selection, physical cosmology, and observer-substance readings.
\item $A$ is the audit row tying $D,M,T,B,J,F$ to the hyperbolic phase vision and to the Poincare-disk metric and transport packets.
\item $H$ records componentwise $\hsame$ transport for disk-coordinate, metric-read, phase-transport, boundary-geodesic, classifier-stability, refusal, and audit rows.
\item $C$ records displayed $\Cont$ replay through finite disk observations, metric reads, phase transport, boundary-geodesic checks, classifier stability, provenance, and refusal.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicGeodesicBoundaryUp$, $\UnitDiskUp$, $\HyperbolicMetricUp$, $\PoincareDiskPhaseTransportUp$, $\UnitaryGroupUp$, $\DynSystemUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicGeodesicBoundaryUp}$ row.
\end{enumerate}
The carrier exports boundary-geodesic data only through these rows. It has no coordinate for a completed hyperbolic plane, quotient ideal boundary, selected horocycle, global physical evolution law, or object-level observer substance.
\end{definition}

\begin{theorem}[HyperbolicGeodesicBoundary NameCert obligations]
\label{thm:hyperbolic-geodesic-boundary-namecert-obligations}
For every accepted $\HyperbolicGeodesicBoundaryUp$ carrier
$$
G=(D,M,T,B,J,F,A,H,C,P,N),
$$
the local $\NameCert_{\HyperbolicGeodesicBoundaryUp}$ surface consists exactly of disk-coordinate admission, hyperbolic-metric read admission, Poincare-disk phase-transport admission, boundary-geodesic incidence, classifier stability, refusal exactness, audit provenance, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.

Every boundary-geodesic consumer must factor through
$$
D,M,T \longmapsto B,J,F,A \longmapsto H,C,P,N.
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-geodesic-boundary-carrier}. The visible surface begins with disk-coordinate row $D$, metric-read row $M$, and phase-transport row $T$.

Read the incidence and stability rows next. The row $B$ records boundary-geodesic incidence as finite far-end evidence, while $J$ preserves the disk, metric, transport, and boundary classifiers across the displayed data.

The refusal and audit rows keep the packet aligned with the hyperbolic phase reading without exporting host geometry. Finally $H,C,P,N$ transport, replay, source, and name only those displayed rows, so no quotient boundary, selected horocycle, physical horizon, or observer-substance reading can be extracted.
\end{proof}

\begin{theorem}[HyperbolicGeodesicBoundary phase handoff]
\label{thm:hyperbolic-geodesic-boundary-phase-handoff}
Every phase-transport consumer of an accepted $\HyperbolicGeodesicBoundaryUp$ carrier receives the geodesic far-end only after the route
$$
\UnitDiskUp,\ \HyperbolicMetricUp,\ \PoincareDiskPhaseTransportUp,\ \UnitaryGroupUp,\ \DynSystemUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert
$$
has been displayed. The consumer may use finite disk coordinates, hyperbolic metric reads, reversible phase transport, finite flow, boundary incidence, classifier stability, provenance, and local naming. It may not read quotient boundary equality, completed geodesic compactification, selected horocycles, physical cosmology, or observer substance.
\end{theorem}
\begin{proof}
Start from the NameCert obligation surface of \autoref{thm:hyperbolic-geodesic-boundary-namecert-obligations}. It places the disk-coordinate row, hyperbolic metric read, and phase-transport route before boundary incidence is exposed.

Use the phase-transport ledger of \autoref{thm:poincare-disk-phase-transport-ledger}. The reversible transport and finite flow rows keep the source ledger visible while the boundary-geodesic row is read.

The hyperbolic metric obligations of \autoref{thm:hyperbolic-metric-namecert-obligations} supply the metric-read discipline. Together with $H,C,P,N$, these rows give a finite phase handoff and no stronger host-side boundary object.
\end{proof}

\falsifiablePrediction{A $\HyperbolicGeodesicBoundaryUp$ consumer that obtains quotient boundary equality, selected horocycle data, or a completed geodesic compactification without first reading the route $D,M,T,B,J,F,A,H,C,P,N$ refutes the carrier surface.}

\independenceWitness{hyperbolic\_metric, unitdisk, unitarygroup, dynsystem, poincare\_disk\_phase\_transport: $\HyperbolicGeodesicBoundaryUp$ is not bijective to any listed sibling because it jointly carries disk-coordinate observations, hyperbolic metric reads, phase transport, boundary-geodesic incidence, classifier stability, refusal, audit provenance, transport, replay, package sourcing, and local NameCert rows.}

The Lean follow-up for this packet must provide explicit $\mathsf{Nontrivial}\ \HyperbolicGeodesicBoundaryUp$ and $\mathsf{FieldFaithful}\ \HyperbolicGeodesicBoundaryUp$ TasteGate instances. Those instances must keep $D,M,T,B,J,F,A,H,C,P,N$ as separate fields before any checked carrier-alignment theorem can serve as a public TasteGate realization.

\closureat{HyperbolicGeodesicBoundaryUp}{seedStr}

\begin{closurestatus}{\HyperbolicGeodesicBoundaryUp}
  \constructivestory{A $\HyperbolicGeodesicBoundaryUp$ packet is generated from UnitDisk disk coordinates, HyperbolicMetric metric reads, PoincareDiskPhaseTransport rows, boundary-geodesic incidence, classifier stability, refusal exactness, audit provenance, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-geodesic-boundary-carrier}, \autoref{thm:hyperbolic-geodesic-boundary-namecert-obligations}, and \autoref{thm:hyperbolic-geodesic-boundary-phase-handoff} seed the finite boundary-geodesic route over disk-coordinate, hyperbolic-metric, phase-transport, and provenance rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient boundary equality, completed geodesic compactification, selected horocycles, physical cosmology, observer-substance readings, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, boundary-geodesic incidence, metric-read stability, phase-transport handoff, refusal exactness, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming for BEDC.Derived.HyperbolicGeodesicBoundaryUp.}
\end{closurestatus}
