\chapter{A Concrete Naming Certificate for $\HyperbolicExpansionLedgerUp$}
\label{ch:concrete-instances-hyperbolic-expansion-ledger-namecert}
\origin{ai}

The $\HyperbolicExpansionLedgerUp$ packet realizes the observer-expansion reading of \autoref{sec:hyperbolic-observer-expansion} as finite BEDC certificate data. It sits after the disk-coordinate surface of \autoref{ch:concrete-instances-unitdisk-namecert}, the complex phase readout of \autoref{ch:concrete-instances-complex-namecert}, the finite flow route of \autoref{ch:concrete-instances-dynsystem-namecert}, the Poincare disk transport packet of \autoref{ch:concrete-instances-poincare-disk-phase-transport-namecert}, and the metric-read packet of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}. The chapter names expansion as a records-side ledger reading, not as global time, physical cosmology, or object-level boundary fixedness.

\begin{definition}[Hyperbolic expansion ledger carrier]
\label{def:hyperbolic-expansion-ledger-carrier}
A $\HyperbolicExpansionLedgerUp$ carrier is a finite $\BHist$ packet
$$
X=(F,D,G,M,B,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the focused-ledger row recording the visible record family whose growth is being read.
\item $D$ is the disk-readout row over $\UnitDiskUp$, $\ComplexUp$, and $\PoincareDiskPhaseTransportUp$ coordinates.
\item $G$ is the $\Cont$-growth row comparing local continuation extension with successive ledger readouts.
\item $M$ is the $\HyperbolicMetricUp$ metric-read row consumed only after $F,D,G$ have been displayed.
\item $B$ is the boundary-refusal row excluding global clock, physical cosmology, completed boundary object, and object-level boundary fixedness.
\item $A$ is the provenance row tying $F,D,G,M,B$ to the hyperbolic observer-expansion reading.
\item $H$ records componentwise $\hsame$ transport for focused-ledger, disk-readout, growth, metric-read, boundary-refusal, provenance, replay, and local naming rows.
\item $C$ records displayed $\Cont$ replay through the focused ledger, disk readout, growth route, metric read, and refusal rows.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicExpansionLedgerUp$, $\PoincareDiskPhaseTransportUp$, $\HyperbolicMetricUp$, $\UnitDiskUp$, $\DynSystemUp$, $\ComplexUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicExpansionLedgerUp}$ row.
\end{enumerate}
The carrier exports expansion only as a finite focused-ledger and metric-read route. It contains no global clock, no empirical cosmology, no completed boundary model, and no object-level fixed boundary.
\end{definition}

\begin{theorem}[Hyperbolic expansion ledger NameCert obligations]
\label{thm:hyperbolic-expansion-ledger-namecert-obligations}
For every accepted $\HyperbolicExpansionLedgerUp$ carrier $X=(F,D,G,M,B,A,H,C,P,N)$, the local $\NameCert_{\HyperbolicExpansionLedgerUp}$ surface consists exactly of focused-ledger admission, disk-readout admission, $\Cont$-growth routing, metric-read admission, boundary-refusal exactness, provenance, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every accepted expansion read factors through
$$
F\longmapsto D\longmapsto G\longmapsto M\longmapsto B\longmapsto A\longmapsto H\longmapsto C\longmapsto P\longmapsto N.
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-expansion-ledger-carrier}. The focused ledger $F$, disk readout $D$, growth row $G$, metric read $M$, and boundary-refusal row $B$ are displayed before provenance and naming are consumed.

Read the route in the stated order. The disk metric is available only after the focused ledger and $\Cont$-growth route have been displayed, so expansion is a records-side reading rather than a global clock.

The rows $A,H,C,P,N$ then record provenance, transport, replay, package sourcing, and local naming. Since no global clock, physical cosmology, completed boundary model, or object-level fixed boundary has a carrier coordinate, none can be exported by the NameCert surface.
\end{proof}

\begin{theorem}[Hyperbolic expansion ledger Cont-growth route]
\label{thm:hyperbolic-expansion-ledger-cont-growth-route}
Every accepted expansion read of a $\HyperbolicExpansionLedgerUp$ packet factors through the focused ledger and $\Cont$-growth route before disk metric consumption:
$$
F,D,G\longmapsto M.
$$
The hyperbolic metric row $M$ may compare displayed disk readouts only after the local continuation-growth row $G$ has been opened, and the boundary-refusal row $B$ prevents the comparison from becoming a global clock, physical cosmology, completed boundary, or object-level fixedness claim.
\end{theorem}
\begin{proof}
Start with a metric consumer of $M$. Carrier projection shows that $M$ is downstream of the focused ledger $F$, disk readout $D$, and continuation-growth row $G$.

Use the displayed $\Cont$ replay row $C$. It can replay metric consumption only along the focused-ledger and growth route, so the disk metric cannot be read as an independent time parameter.

Finally apply boundary-refusal exactness through $B$. The packet refuses global clock, physical cosmology, completed boundary, and object-level fixedness readings, leaving only the finite records-side expansion route.
\end{proof}

\falsifiablePrediction{Every accepted expansion read factors through the focused ledger and $\Cont$-growth route before disk metric consumption; a consumer that reads the hyperbolic metric without $F,D,G$ refutes the $\HyperbolicExpansionLedgerUp$ carrier.}

\independenceWitness{poincare-disk-phase-transport, hyperbolic-metric, unitdisk, dynsystem, complex: no listed sibling is bijective to $\HyperbolicExpansionLedgerUp$ because the packet jointly binds focused-ledger growth, disk readout, Cont-growth routing, metric consumption, boundary refusal, provenance, transport, replay, package sourcing, and local naming.}

The Lean follow-up for this packet must provide explicit $\mathsf{Nontrivial}\ \HyperbolicExpansionLedgerUp$ and $\mathsf{FieldFaithful}\ \HyperbolicExpansionLedgerUp$ TasteGate instances. Those instances must keep $F,D,G,M,B,A,H,C,P,N$ as separate fields before any checked carrier-alignment theorem can serve as a public TasteGate realization.

\closureat{HyperbolicExpansionLedgerUp}{seedStr}

\begin{closurestatus}{\HyperbolicExpansionLedgerUp}
  \constructivestory{A $\HyperbolicExpansionLedgerUp$ packet is generated from a focused-ledger row, disk-readout row, Cont-growth route, HyperbolicMetric read, boundary-refusal row, provenance row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-expansion-ledger-carrier}, \autoref{thm:hyperbolic-expansion-ledger-namecert-obligations}, and \autoref{thm:hyperbolic-expansion-ledger-cont-growth-route} seed the finite observer-expansion route through focused-ledger, disk-readout, Cont-growth, metric-read, boundary-refusal, provenance, transport, replay, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global clock semantics, physical cosmology, completed boundary geometry, object-level boundary fixedness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, focused-ledger rows, disk-readout rows, Cont-growth routing, metric-read rows, boundary-refusal exactness, TasteGate nontriviality, field faithfulness, provenance, and local naming for BEDC.Derived.HyperbolicExpansionLedgerUp.}
\end{closurestatus}
