\chapter{A Concrete Naming Certificate for $\WeakKonigBoundaryUp$}
\label{ch:concrete-instances-weak-konig-boundary-namecert}
\origin{human}

Following Kleene and Bishop--Bridges on finite binary trees, Cantor-space paths, and constructive real completion, the $\WeakKonigBoundaryUp$ packet records the boundary at which finite tree inspection remains available while weak KĂ¶nig path selection is refused as a BEDC primitive. It sits after the finite obstruction surface of \autoref{ch:concrete-instances-kleene-tree-namecert}, the Cantor and FanTheorem interfaces of \autoref{ch:concrete-instances-cantorspace-namecert} and \autoref{ch:concrete-instances-fantheorem-namecert}, the finite window and regular readback route of \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}, and the completion-facing seal rows of \autoref{ch:concrete-instances-real-namecert} and \autoref{ch:concrete-instances-separable-completion-namecert}. The packet names the finite-tree/path-selection boundary used by Real and Completion consumers without turning that boundary into countable choice, quotient stream equality, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[WeakKonigBoundary carrier]
\label{def:weak-konig-boundary-carrier}
A $\WeakKonigBoundaryUp$ carrier is a finite $\BHist$ packet
$$
W=(K,A,F,S,Q,R,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\KleeneTreeUp$ finite-prefix tree packet, including the decidable node ledger and obstruction row of \autoref{def:kleene-tree-carrier}.
\item $A$ is the $\CantorSpaceUp$ finite-prefix observation row offered to consumers that inspect binary path fragments.
\item $F$ is the $\FanTheoremUp$ finite-bar test row available only as displayed finite cover data, not as open-cover compactness.
\item $S$ is the $\StreamNameUp$ finite-window schedule through which every path-like request must pass.
\item $Q$ is the $\RegSeqRatUp$ regular readback row obtained from displayed finite windows before any Real-facing seal is inspected.
\item $R$ is the $\RealUp$ and completion-facing seal row reached only after $K,A,F,S,Q$ have been displayed.
\item $O$ is the boundary-refusal row: no infinite branch selector, no countable-choice functional, no quotient stream equality, no open-cover compactness principle, and no ambient $\RealUp$ completeness theorem is a coordinate of the packet.
\item $H$ records componentwise $\hsame$ transport for the tree packet, Cantor prefix row, fan row, stream windows, regular readback, Real seal, refusal row, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite tree or path request through $K,A,F,S,Q,R,O,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\WeakKonigBoundaryUp$, $\KleeneTreeUp$, $\CantorSpaceUp$, $\FanTheoremUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BoolUp$, $\ListUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\WeakKonigBoundaryUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite tree/path boundary packet. It has no coordinate for an infinite branch, a path-selection functional, countable choice, quotient stream equality, open-cover compactness, selected completion limits, or ambient Real completeness.
\end{definition}

\begin{theorem}[WeakKonigBoundary NameCert obligations]
\label{thm:weak-konig-boundary-namecert-obligations}
For every accepted $\WeakKonigBoundaryUp$ carrier $W=(K,A,F,S,Q,R,O,H,C,P,N)$, the local $\NameCert_{\WeakKonigBoundaryUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the displayed $\KleeneTreeUp$ packet, $\CantorSpaceUp$ prefix row, $\FanTheoremUp$ finite-bar row, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\RealUp$ seal, refusal row, transport, replay, provenance, and local naming;
\item tree-window exactness, requiring every path-like read to pass through the finite tree row $K$ and finite window row $S$ before any Cantor, FanTheorem, RegSeqRat, Real, or Completion-facing row is exposed;
\item regular-readback discipline, requiring the $\RegSeqRatUp$ row $Q$ to be obtained from displayed finite windows rather than from quotient stream equality;
\item seal nonescape, requiring the Real and completion-facing row $R$ to remain downstream of $K,A,F,S,Q$ and the refusal row $O$;
\item boundary refusal, excluding infinite branch selection, countable choice, quotient stream equality, open-cover compactness, and ambient Real completeness from the packet.
\end{enumerate}
No WeakKonigBoundary obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:weak-konig-boundary-carrier}. The projection exposes exactly the Kleene tree packet $K$, Cantor prefix row $A$, FanTheorem finite-bar row $F$, stream windows $S$, regular readback $Q$, Real seal $R$, refusal row $O$, and structural rows $H,C,P,N$.

Tree-window exactness is inherited from the finite route displayed by \autoref{thm:kleene-tree-streamname-path-boundary}. A path-like request first reads the finite tree and the finite stream window; it cannot jump directly to an infinite branch or completed Cantor point.

The regular-readback and seal rows are downstream. The row $Q$ is admitted only after the finite windows are fixed, and the row $R$ is reached only after $K,A,F,S,Q$ and the refusal row have been displayed.

Finally, $H,C,P,N$ transport, replay, source, and name the same finite route. Since none of the carrier rows stores an infinite branch selector, countable-choice functional, quotient stream equality, open-cover compactness object, or ambient Real-completeness theorem, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[WeakKonigBoundary Real-completion refusal]
\label{thm:weak-konig-boundary-real-completion-refusal}
Every Real or Completion-facing consumer of an accepted $\WeakKonigBoundaryUp$ carrier factors through the finite route
$$
K,A,F,S,Q,R,O,H,C,P,N .
$$
Consequently the consumer may reuse finite Kleene-tree prefixes, Cantor-space observations, FanTheorem finite-bar rows, StreamName windows, and RegSeqRat readbacks, but it receives no infinite branch selection, no countable-choice schedule, no quotient stream equality, no open-cover compactness principle, and no ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Begin with a Real or Completion-facing read of $W=(K,A,F,S,Q,R,O,H,C,P,N)$. Carrier admission gives the consumer the tree, Cantor, fan, stream-window, regular-readback, and seal rows only as the displayed finite packet.

Use the Kleene-tree boundary from \autoref{thm:kleene-tree-real-completion-nonescape}. Any Real-facing interpretation of tree data must already pass through finite $\StreamNameUp$ windows and the obstruction row before a real seal is inspected.

The $\WeakKonigBoundaryUp$ carrier adds the refusal row $O$ at the same boundary. Thus the completion-facing row $R$ can be read only after the finite tree/path route and cannot supply a path selector, quotient stream equality, open-cover compactness, or ambient Real completeness.

Transport and replay through $H$ and $C$, with provenance and naming through $P$ and $N$, preserve the displayed route. Therefore every Real or Completion consumer receives the finite boundary package and none of the excluded principles.
\end{proof}

\falsifiablePrediction{A $\WeakKonigBoundaryUp$ consumer that obtains an infinite branch selector, countable-choice schedule, quotient stream equality, open-cover compactness principle, or ambient $\RealUp$ completeness theorem without first reading the displayed route $K,A,F,S,Q,R,O,H,C,P,N$ refutes the carrier surface.}

\independenceWitness{kleene-tree, cantorspace, fantheorem, streamname, regseqrat, real, separable-completion: $\WeakKonigBoundaryUp$ is not bijective to any listed sibling because it jointly carries the finite tree packet, Cantor prefix row, fan row, stream windows, regular readback, Real seal, refusal row, transport, replay, provenance, and local NameCert row in one packet.}

\closureat{WeakKonigBoundaryUp}{seedStr}

\begin{closurestatus}{\WeakKonigBoundaryUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:weak-konig-boundary-carrier}, \autoref{thm:weak-konig-boundary-namecert-obligations}, and \autoref{thm:weak-konig-boundary-real-completion-refusal} seed the finite tree/path-selection boundary separating Real and Completion-facing reads from weak KĂ¶nig path selection.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close weak KĂ¶nig's lemma, infinite branch selection, countable choice, quotient stream equality, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tree-window exactness, regular-readback discipline, seal nonescape, and boundary-refusal proofs for BEDC.Derived.WeakKonigBoundaryUp.}
  \constructivestory{A $\WeakKonigBoundaryUp$ packet is generated from a KleeneTreeUp finite tree packet, CantorSpace finite-prefix row, FanTheorem finite-bar row, StreamName finite windows, RegSeqRat readback, RealUp seal, explicit refusal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
