\chapter{A Concrete Naming Certificate for $\CauchyCutBridgeUp$}
\label{ch:concrete-instances-cauchy-cut-bridge-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\CauchyCutBridgeUp$ packet records the finite handoff by which a regular Cauchy real name supplies located-cut observations without identifying either presentation by quotient equality. It sits between the regular-rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, the located-cut surface of \autoref{ch:concrete-instances-locatedcut-namecert}, the dyadic arithmetic ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a bridge for displayed approximation data, not a Dedekind-completeness theorem or an equality principle for completed reals.

\begin{definition}[Cauchy-cut bridge carrier]
\label{def:cauchy-cut-bridge-carrier}
A $\CauchyCutBridgeUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,L,D,W,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\RegSeqRatUp$ readback row naming the regular Cauchy rational source.
\item $L$ is the $\LocatedCutUp$ row recording the lower and upper located observations obtained from the same regular name.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare regular readbacks with located lower--upper brackets.
\item $W$ is the $\StreamNameUp$ window schedule listing the finite precision rows at which the regular name and located cut are jointly inspected.
\item $E$ is the terminal $\RealUp$ seal row, read only after $Q,L,D,W$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the regular readback, located-cut row, dyadic ledger, stream windows, Real seal, replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay of the bridge route
$$
Q,W,D \longmapsto L \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCutBridgeUp$, $\RegSeqRatUp$, $\LocatedCutUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCutBridgeUp}$ row.
\end{enumerate}
The carrier contains no coordinate for quotient reals, Dedekind completeness, host equality of real names, trichotomy, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[Cauchy-cut bridge NameCert obligations]
\label{thm:cauchy-cut-bridge-namecert-obligations}
For every accepted $\CauchyCutBridgeUp$ carrier $B=(Q,L,D,W,E,H,C,P,N)$, the local $\NameCert_{\CauchyCutBridgeUp}$ surface consists exactly of carrier admission for the displayed regular readback, located-cut row, dyadic tolerance ledger, stream-window schedule, Real seal, componentwise transport, continuation replay, package provenance, and local naming row; regular-to-located exposure through $Q,W,D,L$; Real-seal exposure through $E$; and refusal of quotient reals, Dedekind-completeness claims, host equality, trichotomy, choice, and ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-cut-bridge-carrier}. The visible rows are exactly $Q,L,D,W,E,H,C,P,N$, so carrier admission exposes the regular readback, located-cut observation, dyadic ledger, stream schedule, terminal seal, and structural rows.

The bridge exposure is supplied by the replay row $C$. It first reads the regular name through $Q$ and the finite windows $W$, then checks the matching dyadic tolerances in $D$, and only then exposes the located-cut row $L$.

The Real seal and structural rows are downstream of that route. Transport through $H$, provenance through $P$, and local naming through $N$ record the same finite bridge, while no refused object appears as a carrier coordinate.
\end{proof}

\begin{theorem}[Cauchy-cut bridge regular-located handoff]
\label{thm:cauchy-cut-bridge-regular-located-handoff}
Let $B=(Q,L,D,W,E,H,C,P,N)$ be an accepted $\CauchyCutBridgeUp$ carrier. Every located-cut observation exported by $B$ factors through the finite handoff
$$
Q,W,D \longmapsto L \longmapsto E,H,C,P,N .
$$
Thus the bridge reads the regular Cauchy name through $\RegSeqRatUp$, finite $\StreamNameUp$ windows, and $\DyadicRatCoreUp$ tolerance rows before the $\LocatedCutUp$ data or the terminal $\RealUp$ seal can be consumed. It does not export quotient reals, Dedekind completeness, host equality, trichotomy, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with a consumer of the located-cut row. The carrier definition gives $L$ only as a displayed row of $B$, and the continuation row records that it is reached from $Q,W,D$.

Use the sibling routes cited in the chapter introduction. $\RegSeqRatUp$ supplies regular rational readback, $\StreamNameUp$ supplies finite windows, and $\DyadicRatCoreUp$ supplies the tolerance comparison that turns the readback into lower--upper located observations.

Finally read the terminal seal row $E$ and the structural rows $H,C,P,N$. They transport, replay, source, and name the same handoff; none of them stores quotient equality, a Dedekind-completeness witness, a host equality test, trichotomy, choice, or ambient completeness.
\end{proof}

\begin{closurestatus}{\CauchyCutBridgeUp}
  \constructivestory{A $\CauchyCutBridgeUp$ packet is generated from a $\RegSeqRatUp$ readback row, a $\LocatedCutUp$ observation row, a $\DyadicRatCoreUp$ tolerance ledger, finite $\StreamNameUp$ windows, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-cut-bridge-carrier}, \autoref{thm:cauchy-cut-bridge-namecert-obligations}, and \autoref{thm:cauchy-cut-bridge-regular-located-handoff} seed the finite bridge from regular Cauchy readbacks to located-cut observations over $\RegSeqRatUp$, $\LocatedCutUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient reals, Dedekind-completeness claims, host equality of real names, trichotomy, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires carrier admission, regular-to-located exposure, tolerance exactness, Real-seal nonescape, and ledger-refusal proofs for the same finite packet.}
\end{closurestatus}
