\chapter{A Concrete Naming Certificate for $\MetacicRedexChoiceFrontierUp$}
\label{ch:concrete-instances-metacic-redex-choice-frontier-namecert}
\origin{ai}

The $\MetacicRedexChoiceFrontierUp$ packet realizes the MetaCIC audit-map frontier of \autoref{ch:visions-subhub-metacic} as finite BEDC rows. It sits next to the redex frontier, normalization frontier, confluence-audit packet, and decidable-boundary anchors already used by the MetaCIC vision, but it names the smaller object needed by a candidate-mediated reducer: a displayed finite choice surface for which redex rows may be inspected, which normalization and confluence-audit rows are available, and which boundaries remain undecided. The packet consumes the redex-row surface of \autoref{ch:concrete-instances-metacic-redex-frontier-namecert}, the candidate-normalization boundary of \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, the local critical-pair fork surface of \autoref{ch:concrete-instances-metacic-frontier-critical-pair-namecert}, and the beta critical-pair row of \autoref{ch:concrete-instances-beta-critical-pair-namecert}. The normal-form endpoint row is consumed through \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert}, while the redex-choice packet keeps subject reduction and global consistency outside the carrier. The packet does not assert global normalization, Church--Rosser, subject reduction for all terms, or a complete MetaCIC semantics.

\begin{definition}[MetaCIC redex-choice frontier carrier]
\label{def:metacic-redex-choice-frontier-carrier}
A $\MetacicRedexChoiceFrontierUp$ carrier is a finite $\BHist$ packet
$$
R=(A,N,F,D,B,H,K,L,C,P,Q)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the MetaCIC redex row, listing the candidate redexs exposed by the local term-and-context window.
\item $N$ is the normalization-frontier row, recording which candidates have a displayed bounded reduction trace.
\item $F$ is the confluence-audit row, recording local fork and join checks for the same candidate set.
\item $D$ is the decidable-boundary row, recording which redex choices are classified by finite inspection and which remain outside the packet.
\item $B$ is the $\BHist$ replay ledger for the term window, candidate row, trace row, fork row, boundary row, and local naming row.
\item $H$ records componentwise $\hsame$ transport for the redex, normalization, confluence-audit, decidability, replay, continuation, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay from a term-window request through $A,N,F,D,B,H,P,Q$.
\item $L$ is the $\Pkg$ provenance over $\MetacicRedexChoiceFrontierUp$, MetaCIC redex rows, normalization-frontier rows, confluence-audit rows, decidable-boundary rows, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $C$ records the candidate-choice classifier: it exposes only the redex choices whose $A,N,F,D$ rows are present in the packet.
\item $P$ records the local package boundary for Nontrivial and FieldFaithful TasteGate instances to be checked by a later Lean development over the displayed carrier.
\item $Q$ is the local $\NameCert_{\MetacicRedexChoiceFrontierUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,N,F,D,B,H,K,L,C,P,Q$. It has no coordinate for global normalization, global confluence, unrestricted redex selection, subject reduction for all terms, quotient syntax, host evaluator soundness, or a completed MetaCIC model.
\end{definition}

\begin{theorem}[MetaCIC redex-choice frontier NameCert obligations]
\label{thm:metacic-redex-choice-frontier-namecert-obligations}
For every accepted $\MetacicRedexChoiceFrontierUp$ carrier
$$
R=(A,N,F,D,B,H,K,L,C,P,Q),
$$
the local $\NameCert_{\MetacicRedexChoiceFrontierUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier exposure for MetaCIC redex rows, normalization-frontier traces, confluence-audit fork rows, decidable-boundary classifiers, replay, transport, continuation, provenance, candidate-choice, TasteGate boundary, and local naming rows;
\item redex-choice classification, requiring the candidate-choice row $C$ to inspect only redexs displayed in $A$ and only boundary outcomes displayed in $D$;
\item normalization-frontier compatibility, requiring every candidate exported by $C$ to carry either the bounded trace row in $N$ or the explicit boundary refusal in $D$;
\item confluence-audit compatibility, requiring every fork exported by $C$ to use the same candidate set as $A$ and the same local fork rows as $F$;
\item TasteGate preparation, requiring the packet to expose the Nontrivial and FieldFaithful instance boundary in $P$ without claiming those Lean instances as paper-side evidence;
\item ledger refusal for global normalization, global confluence, unrestricted redex selection, subject reduction for all terms, quotient syntax, host evaluator soundness, and a completed MetaCIC model.
\end{enumerate}
No redex-choice frontier obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The term-facing data are the redex row $A$, the normalization-frontier row $N$, the confluence-audit row $F$, the decidable-boundary row $D$, and the candidate-choice row $C$.

The candidate classifier cannot inspect a redex outside $A$, because $C$ is downstream of the displayed redex row. It cannot treat an undecided boundary as decided, because every exported choice must pass through $D$.

The normalization and confluence rows are tied to the same candidate set. A selected candidate therefore carries the bounded trace information from $N$ and the local fork information from $F$ exactly when those rows are displayed by the packet.

The TasteGate boundary row $P$ records the intended Nontrivial and FieldFaithful instance surface for Lean without adding a marker or treating the instances as verified. The refused global principles have no carrier coordinate, so the NameCert surface remains finite.
\end{proof}

\begin{theorem}[MetaCIC redex-choice frontier nonescape]
\label{thm:metacic-redex-choice-frontier-nonescape}
Every reducer-facing read from an accepted $\MetacicRedexChoiceFrontierUp$ packet factors through
$$
A,N,F,D \longmapsto C \longmapsto B,H,K,L,P,Q .
$$
The exported object is a finite candidate-mediated frontier for local redex choice, not global normalization, global confluence, unrestricted redex selection, quotient syntax, host evaluator soundness, or a completed MetaCIC model.
\end{theorem}
\begin{proof}
Start with the displayed redex, normalization, confluence-audit, and decidable-boundary rows. These rows are the only inputs to the candidate-choice classifier.

The classifier $C$ exports only the candidates that survive those displayed rows. Replay through $B$, transport through $H$, continuation through $K$, provenance through $L$, TasteGate boundary through $P$, and naming through $Q$ preserve the same finite route.

Since no global normalization theorem, global confluence theorem, unrestricted redex selector, quotient syntax object, host evaluator soundness proof, or completed MetaCIC model appears in the carrier, the reducer-facing read cannot escape the finite frontier.
\end{proof}

\falsifiablePrediction{A $\MetacicRedexChoiceFrontierUp$ reducer-facing read factors through displayed MetaCIC redex rows, normalization-frontier traces, confluence-audit fork rows, decidable-boundary classifiers, candidate-choice rows, BHist replay, hsame transport, Cont replay, Pkg provenance, TasteGate boundary rows, and local NameCert data.}

\independenceWitness{metacic-redex, metacic-normalization-frontier, metacic-confluence-audit, metacic-decidable-boundary: $\MetacicRedexChoiceFrontierUp$ is not bijective to any listed anchor because it jointly carries candidate-choice classification, shared redex-boundary routing, Nontrivial and FieldFaithful TasteGate boundaries, replay, transport, provenance, and local naming.}

\closureat{MetacicRedexChoiceFrontierUp}{seedStr}

\begin{closurestatus}{\MetacicRedexChoiceFrontierUp}
  \constructivestory{A $\MetacicRedexChoiceFrontierUp$ packet is generated from MetaCIC redex rows, normalization-frontier rows, confluence-audit rows, decidable-boundary rows, BHist replay, componentwise hsame transport, displayed Cont replay, Pkg provenance, a candidate-choice classifier, Nontrivial and FieldFaithful TasteGate boundary rows, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-redex-choice-frontier-carrier}, \autoref{thm:metacic-redex-choice-frontier-namecert-obligations}, and \autoref{thm:metacic-redex-choice-frontier-nonescape} seed the finite candidate-mediated redex-choice frontier for MetaCIC audit maps.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global normalization, global confluence, unrestricted redex selection, subject reduction for all terms, quotient syntax, host evaluator soundness, a completed MetaCIC model, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, redex-choice classification, normalization-frontier compatibility, confluence-audit compatibility, Nontrivial and FieldFaithful TasteGate instances, non-escape, transport, replay, provenance, and local naming for BEDC.Derived.MetacicRedexChoiceFrontierUp.}
\end{closurestatus}
