\chapter{A Concrete Naming Certificate for $\RatCauchyCompletionUp$}
\label{ch:concrete-instances-rat-cauchy-completion-namecert}
\origin{human}

Following Bishop and Bridges' constructive treatment of the real line as regular Cauchy data over the rationals, the $\RatCauchyCompletionUp$ packet records the finite BEDC interface by which rational rows are read as regular rational Cauchy names and then presented to the real-name seal. It consumes the rational source surface of \autoref{ch:concrete-instances-rat-namecert}, the Cauchy-modulus tail budget of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite schedule surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal $\RealUp$ seal boundary of \autoref{ch:concrete-instances-real-namecert}. The packet gives Phase Real and Completion consumers a named rational-Cauchy handoff without quotienting Cauchy names, selecting limits, invoking countable choice, or asserting ambient completeness of $\RealUp$.

\begin{definition}[RatCauchyCompletion carrier]
\label{def:rat-cauchy-completion-carrier}
A $\RatCauchyCompletionUp$ carrier is a finite $\BHist$ packet
$$
C=(R,M,S,Q,D,E,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RatUp$ source row, recording the rational entries that seed the completion-facing stream.
\item $M$ is the $\CauchyModulusUp$ tail row, recording the displayed budget by which two sufficiently late rational observations are forced inside the requested tolerance.
\item $S$ is the $\StreamNameUp$ schedule row, recording the finite windows through which later consumers request rational approximants.
\item $Q$ is the $\RegSeqRatUp$ readback row, recording the regular rational sequence visible to the completion corridor.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic budgets, endpoint comparisons, and finite error rows used to check the regularity bounds.
\item $E$ is the $\RealUp$ seal row, recording only the handoff boundary at which the regular rational name may be read as a real-facing name.
\item $H$ records componentwise $\hsame$ transport for the rational source, tail budget, schedule, regular readback, dyadic ledger, seal, continuation, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ routes from rational source rows through tail budgets, schedules, regular readback, dyadic tolerance checks, and the real-seal boundary.
\item $P$ is the $\Pkg$ provenance over $\RatCauchyCompletionUp$, $\RatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RatCauchyCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,M,S,Q,D,E,H,K,P,N$. It has no coordinate for quotient-real equality, selected limits, arbitrary Cauchy filters, countable-choice schedules, host completeness, or a theorem that every $\RealUp$ request is complete.
\end{definition}

\begin{theorem}[RatCauchyCompletion NameCert obligations]
\label{thm:rat-cauchy-completion-namecert-obligations}
For every accepted $\RatCauchyCompletionUp$ carrier
$$
C=(R,M,S,Q,D,E,H,K,P,N),
$$
the local $\NameCert_{\RatCauchyCompletionUp}$ surface consists exactly of carrier exposure for the rational source row $R$, Cauchy-modulus tail row $M$, stream schedule row $S$, regular rational readback row $Q$, dyadic tolerance ledger $D$, real-seal boundary $E$, componentwise transport row $H$, continuation row $K$, package provenance row $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:rat-cauchy-completion-carrier}. Each row named in the statement is one coordinate of the finite packet, and the definition lists no hidden coordinate for completion beyond those rows.

The rational source and Cauchy-modulus obligations are $R$ and $M$. The stream and regular-readback obligations are $S$ and $Q$. The dyadic ledger and real-facing seal obligations are $D$ and $E$.

Transport, replay, provenance, and local naming are supplied by $H,K,P,N$. Repacking these coordinates yields the displayed $\NameCert_{\RatCauchyCompletionUp}$ surface, while any claim about quotient equality, selected limits, countable choice, or ambient $\RealUp$ completeness remains outside the packet.
\end{proof}

\begin{theorem}[RatCauchyCompletion Real seal boundary]
\label{thm:rat-cauchy-completion-real-seal-boundary}
An accepted $\RatCauchyCompletionUp$ carrier may hand its regular rational readback row $Q$ and dyadic tolerance ledger $D$ to the $\RealUp$ seal row $E$ only through the displayed continuation row $K$. The handoff preserves the rational-Cauchy interface for Phase Real and Completion consumers, but it does not assert that $\RealUp$ is complete, does not choose a quotient representative, and does not manufacture a limit outside the rows $R,M,S,Q,D,E,H,K,P,N$.
\end{theorem}
\begin{proof}
The only real-facing coordinate of the carrier is $E$, and the only route into that coordinate is the displayed continuation row $K$. Thus a consumer reaches the seal boundary by reading the rational source, tail budget, stream schedule, regular rational readback, and dyadic ledger through the packet's finite route.

The carrier definition also lists the negative boundary: no coordinate stores a selected limit, a quotient representative, a countable-choice schedule, or an ambient completeness theorem for $\RealUp$. Therefore the seal row is a handoff boundary for existing regular rational data, not a proof of completeness of the target interface.
\end{proof}

\closureat{RatCauchyCompletionUp}{seedStr}

\begin{closurestatus}{\RatCauchyCompletionUp}
  \constructivestory{A $\RatCauchyCompletionUp$ packet is generated from $\RatUp$ source rows, $\CauchyModulusUp$ tail data, $\StreamNameUp$ schedules, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledgers, $\RealUp$ seal rows, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rat-cauchy-completion-carrier}, \autoref{thm:rat-cauchy-completion-namecert-obligations}, and \autoref{thm:rat-cauchy-completion-real-seal-boundary} bind the carrier, local NameCert obligations, and Real-facing seal boundary for the rational-Cauchy completion interface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not prove $\RealUp$ completeness, quotient Cauchy equality, selected limits, arbitrary Cauchy-filter completion, countable choice, or a public standard bridge.}
  \upgradepath{Scoped closure requires Lean encoding of the carrier, the NameCert obligation surface, the Real seal boundary, and the rejection of completeness claims outside the displayed rows.}
\end{closurestatus}
