\chapter{A Concrete Naming Certificate for $\BishopOrderCompletionUp$}
\label{ch:concrete-instances-bishop-order-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopOrderCompletionUp$ packet records the order-completion face of the real-number construction as finite BEDC NameCert data. It sits after the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the comparison boundary of \autoref{ch:concrete-instances-located-real-comparison-namecert}, the lower and upper cut rows of \autoref{ch:concrete-instances-lowerreal-namecert} and \autoref{ch:concrete-instances-lower-upper-real-cut-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a constructive order-completion interface; it is not a quotient-cut construction, selected supremum principle, trichotomy oracle, host real equality test, countable-choice selector, or ambient $\RealUp$ completeness theorem.

\begin{definition}[Bishop order-completion carrier]
\label{def:bishop-order-completion-carrier}
A $\BishopOrderCompletionUp$ carrier is a finite $\BHist$ packet
$$
O=(D,S,R,E,B,L,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ tolerance and comparison-budget ledger used by all lower, upper, and real-seal requests.
\item $S$ is the $\StreamNameUp$ finite-window row inspected at those dyadic requests.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed stream windows.
\item $E$ is the $\RealUp$ seal reached only after $D,S,R$ have been displayed.
\item $B$ is the $\BishopRealComparisonUp$ comparison row, read through the located-real comparison surface and tied to the same windows and dyadic budgets.
\item $L$ is the LowerReal-style located lower-cut ledger, recording only the displayed inhabited lower observations and downward-use rows available to the packet.
\item $U$ is the UpperReal-style located upper-cut ledger, recording only the displayed upper observations and upward-use rows available to the packet.
\item $H$ records componentwise $\hsame$ transport for the tolerance, window, readback, Real seal, comparison, lower-cut, upper-cut, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each order-completion request through $D,S,R,E,B,L,U,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopOrderCompletionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRealComparisonUp$, $\LowerRealUp$, $\UpperRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopOrderCompletionUp}$ row.
\end{enumerate}
The carrier predicate compares accepted packets only through $D,S,R,E,B,L,U,H,C,P,N$. It has no coordinate for quotient cuts, host supremum objects, selected representatives, trichotomy, host real equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop order-completion NameCert obligations]
\label{thm:bishop-order-completion-namecert-obligations}
For every accepted $\BishopOrderCompletionUp$ carrier $O=(D,S,R,E,B,L,U,H,C,P,N)$, the local $\NameCert_{\BishopOrderCompletionUp}$ surface consists exactly of carrier admission, DyadicRatCore tolerance exposure, finite StreamName window exposure, RegSeqRat readback, Real seal handoff, BishopRealComparison exposure, LowerReal-style lower-cut exposure, UpperReal-style upper-cut exposure, componentwise transport, displayed continuation replay, package provenance, and local naming. Every order-completion consumer factors through
$$
D\longmapsto S\longmapsto R\longmapsto E\longmapsto B\longmapsto (L,U)\longmapsto H\longmapsto C\longmapsto P\longmapsto N.
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-order-completion-carrier}. Its real-facing rows are the dyadic tolerance ledger, finite stream windows, regular rational readback, and terminal Real seal.

Read the order rows after the same real-facing route. The comparison row $B$ uses the displayed windows and dyadic budgets, while $L$ and $U$ record the lower and upper located-cut observations available to the packet.

The structural rows then preserve this ordered route. The $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows transport, replay, source, and name the route, and the refused quotient, host-supremum, selected, trichotomy, host-equality, choice, and ambient-completeness objects have no carrier coordinate.
\end{proof}

\begin{theorem}[Bishop order-completion located-cut handoff]
\label{thm:bishop-order-completion-located-cut-handoff}
Every located lower-or-upper cut read exported by an accepted $\BishopOrderCompletionUp$ carrier is downstream of the displayed $\DyadicRatCoreUp$ tolerance ledger, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\RealUp$ seal, and $\BishopRealComparisonUp$ comparison row. The handoff exposes the LowerReal-style and UpperReal-style ledgers only as the finite packet $D,S,R,E,B,L,U,H,C,P,N$.
\end{theorem}
\begin{proof}
Start with the NameCert obligations. They place $D,S,R,E$ before any order-facing row can be consumed.

Next read the comparison boundary. The row $B$ ties lower and upper observations to the same finite windows and dyadic budgets, so the lower and upper ledgers cannot be inspected as independent host cuts.

Finally project $L$ and $U$. These rows are named only inside the carrier and are preserved by $H,C,P,N$, so the handoff contains no quotient-cut equality, selected representative, trichotomy branch, host supremum, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Bishop order-completion Cauchy-cut comparison]
\label{thm:bishop-order-completion-cauchy-cut-comparison}
For every accepted $\BishopOrderCompletionUp$ carrier, the comparison between regular-Cauchy real data and located lower--upper cut data is a single finite route through
$$
\DyadicRatCoreUp\longmapsto\StreamNameUp\longmapsto\RegSeqRatUp\longmapsto\RealUp\longmapsto\BishopRealComparisonUp\longmapsto(\LowerRealUp,\UpperRealUp).
$$
Thus a Cauchy-facing consumer and a cut-facing consumer read the same packet-local rows $D,S,R,E,B,L,U,H,C,P,N$, rather than two unrelated completion principles.
\end{theorem}
\begin{proof}
Read the Cauchy-facing side first. The rows $D,S,R,E$ display the tolerance, window, readback, and Real seal route used by regular-Cauchy consumers.

Read the cut-facing side through the comparison row. The row $B$ is downstream of the same route and supplies the finite comparison request before $L$ and $U$ can expose lower and upper located observations.

The two faces are therefore synchronized by the structural rows. Transport, continuation, provenance, and local naming preserve one packet-local route, while quotient-cut completion, selected supremum, host real equality, trichotomy, countable choice, and ambient Real completeness remain outside the carrier.
\end{proof}

\falsifiablePrediction{A claimed $\BishopOrderCompletionUp$ consumer that reaches a lower-cut or upper-cut row without the displayed DyadicRatCore, StreamName, RegSeqRat, Real, and BishopRealComparison rows refutes the carrier surface.}

\independenceWitness{dyadicratcore, streamname, regseqrat, real, bishoprealcomparison, lowerreal, upperreal: no listed sibling supplies the whole $\BishopOrderCompletionUp$ packet, because each sibling contributes only tolerance, window, readback, seal, comparison, or one-sided cut data while this chapter binds all of them with transport, replay, provenance, and local naming.}

\closureat{BishopOrderCompletionUp}{seedStr}

\begin{closurestatus}{\BishopOrderCompletionUp}
  \constructivestory{A $\BishopOrderCompletionUp$ packet is generated from a DyadicRatCore tolerance ledger, StreamName finite windows, RegSeqRat readback, RealUp seal, BishopRealComparison row, LowerReal-style and UpperReal-style located cut rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-order-completion-carrier}, \autoref{thm:bishop-order-completion-namecert-obligations}, \autoref{thm:bishop-order-completion-located-cut-handoff}, and \autoref{thm:bishop-order-completion-cauchy-cut-comparison} seed the finite order-completion interface joining regular-Cauchy real data to located lower and upper cut rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, quotient cut completion, selected suprema, trichotomy, countable choice, host real equality, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, tolerance-window exactness, regular readback, RealUp seal handoff, comparison-row stability, located cut handoff, Cauchy-cut comparison, transport, replay, provenance, and local naming for BEDC.Derived.BishopOrderCompletionUp.}
\end{closurestatus}
