\chapter{A Concrete Naming Certificate for $\SpeckerSequenceBoundaryUp$}
\label{ch:concrete-instances-specker-sequence-boundary-namecert}
\origin{human}

Following Specker's constructive counterexample tradition and Bishop--Bridges constructive analysis, the $\SpeckerSequenceBoundaryUp$ packet isolates the reusable nonlocated-supremum obstruction behind monotone bounded rational streams. It sits after $\SpeckerSequenceUp$ in \autoref{ch:concrete-instances-speckersequence-namecert} and reads only the finite windows supplied by $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\LocatedCutUp$ in \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-real-namecert}, and \autoref{ch:concrete-instances-locatedcut-namecert}. The packet names the obstruction surface; it does not supply Real completeness, a located supremum, trichotomy, quotient stream equality, countable choice, or selected limits.

\begin{definition}[Specker sequence boundary carrier]\label{def:specker-sequence-boundary-carrier}
A $\SpeckerSequenceBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(S,W,D,M,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SpeckerSequenceUp$ source row naming the monotone bounded rational stream and its nonlocated-supremum boundary.
\item $W$ is the $\StreamNameUp$ schedule selecting the finite source windows inspected by the boundary packet.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and bound ledger read from the same selected windows.
\item $M$ is the monotone and bounded obstruction ledger recording the displayed comparison and bound data that can be read before any real-facing seal.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational windows certified by $S,W,D,M$.
\item $L$ is the $\RealUp$ seal or $\LocatedCutUp$ refusal row; it records that the displayed windows may be sealed as finite real readback data, while a located-cut or supremum witness remains external.
\item $H$ stores componentwise $\hsame$ transport for the source, schedule, dyadic ledger, obstruction ledger, regular readback, seal-or-refusal row, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from $S,W$ into $D$, from $D$ into $M$, from $M$ into $R$, and from $R$ into the seal-or-refusal row $L$.
\item $P$ is the $\Pkg$ provenance over $\SpeckerSequenceBoundaryUp$, $\SpeckerSequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\LocatedCutUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SpeckerSequenceBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,W,D,M,R,L,H,C,P,N$. It has no coordinate for a located supremum, a selected limiting real, quotient stream equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Specker sequence boundary NameCert obligations]\label{thm:specker-sequence-boundary-namecert-obligations}
For every accepted $\SpeckerSequenceBoundaryUp$ carrier $B=(S,W,D,M,R,L,H,C,P,N)$, the local $\NameCert_{\SpeckerSequenceBoundaryUp}$ surface consists exactly of source admission through $S$, finite schedule selection through $W$, dyadic tolerance and bound admission through $D$, monotone bounded obstruction admission through $M$, regular rational readback through $R$, the $\RealUp$ seal or $\LocatedCutUp$ refusal row $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:specker-sequence-boundary-carrier}. The analytic rows are exactly the Specker source, stream schedule, dyadic ledger, monotone bounded obstruction ledger, regular readback, and seal-or-refusal row.

The structural rows $H,C,P,N$ transport, replay, source, and name those same coordinates. Since the carrier contains no further analytic field, the listed rows exhaust the local NameCert obligations.

The missing fields are also part of the boundary. A located supremum, quotient stream equality, countable-choice selector, trichotomy branch, or selected limit would require an additional coordinate, and no such coordinate is present.
\end{proof}

\begin{theorem}[Specker sequence boundary Cauchy readback]\label{thm:specker-sequence-boundary-cauchy-readback}
Every Cauchy-facing read from an accepted $\SpeckerSequenceBoundaryUp$ carrier factors through
$$
S,W\longmapsto D\longmapsto M\longmapsto R\longmapsto L
$$
together with $H,C,P,N$. The row $R$ exports only the $\RegSeqRatUp$ window readback certified by the displayed schedule and dyadic ledger, and the row $L$ exports only a finite $\RealUp$ seal or a $\LocatedCutUp$ refusal boundary.
\end{theorem}
\begin{proof}
Start with the source route. The $\SpeckerSequenceUp$ row $S$ and the $\StreamNameUp$ schedule $W$ determine which finite rational windows are inspected.

Read the dyadic and obstruction ledgers next. The row $D$ supplies the tolerance and bound data for those windows, while $M$ records the monotone bounded obstruction information available at the same finite stages.

The regular readback row $R$ is downstream of those data, and the seal-or-refusal row $L$ is downstream of $R$. Transport, replay, provenance, and local naming through $H,C,P,N$ preserve this route, so no located supremum or selected limiting real is produced by the Cauchy readback.
\end{proof}

\begin{theorem}[Specker sequence boundary nonescape]\label{thm:specker-sequence-boundary-nonescape}
Every consumer of an accepted $\SpeckerSequenceBoundaryUp$ carrier receives only the finite rows $S,W,D,M,R,L,H,C,P,N$. Consequently the packet may reuse the $\SpeckerSequenceUp$ nonlocated-supremum obstruction and its $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\LocatedCutUp$ interfaces, but it exports no $\RealUp$ completeness principle, located supremum, trichotomy, quotient stream equality, countable-choice selector, or selected limit.
\end{theorem}
\begin{proof}
Use \autoref{thm:specker-sequence-boundary-namecert-obligations} to identify the complete public surface of the accepted packet. All analytic reads pass through the six displayed rows $S,W,D,M,R,L$.

Use \autoref{thm:specker-sequence-boundary-cauchy-readback} to order those rows. The regular readback and seal-or-refusal row appear only after finite windows, dyadic data, and monotone bounded obstruction data have been displayed.

Finally read the structural rows. Componentwise transport, displayed replay, provenance, and local naming do not add analytic coordinates, so none of the excluded completeness, choice, equality, order-decision, or selected-limit principles can escape from the packet.
\end{proof}

\falsifiablePrediction{Every $\SpeckerSequenceBoundaryUp$ Cauchy-facing read factors through a SpeckerSequence source row, StreamName schedule, DyadicRatCore tolerance ledger, monotone bounded obstruction ledger, RegSeqRat readback, Real seal or LocatedCut refusal row, transport, continuation, provenance, and local naming.}

\independenceWitness{speckersequence, streamname, regseqrat, dyadicratcore, real, locatedcut: $\SpeckerSequenceBoundaryUp$ is not bijective to any listed sibling because it jointly carries the nonlocated-supremum obstruction route, regular readback, seal-or-refusal boundary, transport, continuation, provenance, and local naming.}

\closureat{SpeckerSequenceBoundaryUp}{seedStr}

\begin{closurestatus}{\SpeckerSequenceBoundaryUp}
  \constructivestory{A $\SpeckerSequenceBoundaryUp$ packet is generated from a $\SpeckerSequenceUp$ source row, a $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ tolerance and bound rows, a monotone bounded obstruction ledger, a $\RegSeqRatUp$ readback row, a $\RealUp$ seal or $\LocatedCutUp$ refusal row, componentwise transport, continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:specker-sequence-boundary-carrier}, \autoref{thm:specker-sequence-boundary-namecert-obligations}, \autoref{thm:specker-sequence-boundary-cauchy-readback}, and \autoref{thm:specker-sequence-boundary-nonescape} bind the finite nonlocated-supremum obstruction certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, located supremum construction, trichotomy, quotient stream equality, countable choice, selected limits, bridge checking, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, NameCert obligations, Cauchy readback, nonescape, and TasteGate field faithfulness for BEDC.Derived.SpeckerSequenceBoundaryUp.}
\end{closurestatus}
