\chapter{A Concrete Naming Certificate for $\MetricCompletionFiniteCoproductUp$}
\label{ch:concrete-instances-metric-completion-finite-coproduct-namecert}
\origin{human}

Following Bishop and Bridges constructive completion theory, the $\MetricCompletionFiniteCoproductUp$ packet records the finite route by which a displayed finite coproduct of metric sources is read before any completion-facing or real-facing consumer may inspect the completed object. It sits after the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the finite sum carrier of \autoref{ch:concrete-instances-sum-namecert}, the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite coproduct completion handoff, not a quotient completion equality, not a selected limit, not a countable-choice selector, and not ambient $\RealUp$ completeness.

\begin{definition}[Metric completion finite-coproduct carrier]
\label{def:metric-completion-finite-coproduct-carrier}
A $\MetricCompletionFiniteCoproductUp$ carrier is a finite $\BHist$ packet
$$
\mathsf{MCFC}(I,S,M,W,R,A,J,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite index row naming the admitted summands.
\item $S$ is the $\SumUp$ coproduct row, recording injections, finite case analysis, and the branch classifier.
\item $M$ is the family of $\MetricCompletionUp$ source rows, one for each admitted branch.
\item $W$ is the $\StreamNameUp$ window row used when a branch request is inspected by a completion consumer.
\item $R$ is the $\RegSeqRatUp$ readback row for the branch-local tolerance and distance data.
\item $A$ is the terminal $\RealUp$ seal reached only after $W$ and $R$ have fixed the requested branch data.
\item $J$ is the coproduct-completion join row, stating that every accepted consumer first selects a displayed finite branch and then reads the corresponding completion route.
\item $H$ records componentwise $\hsame$ transport for index, sum, completion, window, readback, seal, join, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a coproduct-completion request through $I,S,M,W,R,A,J$.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionFiniteCoproductUp$, $\MetricCompletionUp$, $\SumUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricCompletionFiniteCoproductUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,S,M,W,R,A,J,H,C,P,N$. It has no coordinate for quotient completion equality, selected representatives, infinite coproducts, countable choice, host case analysis outside $S$, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Metric completion finite-coproduct NameCert obligations]
\label{thm:metric-completion-finite-coproduct-namecert-obligations}
For every accepted $\MetricCompletionFiniteCoproductUp$ carrier $\mathsf{MCFC}(I,S,M,W,R,A,J,H,C,P,N)$, the local $\NameCert_{\MetricCompletionFiniteCoproductUp}$ surface consists exactly of carrier admission for the finite index row, $\SumUp$ coproduct row, branchwise $\MetricCompletionUp$ rows, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\RealUp$ seal, coproduct-completion join, componentwise transport, displayed replay, provenance, and local naming.

Every obligation is branch-local after the finite case split in $S$, and every public read must pass through $W,R,A$ before it may expose a completed coproduct branch. No obligation is stored in quotient completion equality, selected representatives, countable choice, infinite coproduct data, host case analysis, or ambient completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:metric-completion-finite-coproduct-carrier}. The tuple displays the finite index row, sum row, branchwise completion rows, numerical readback rows, join row, and structural support.

The finite case split is the row $S$. Once a branch is selected, the corresponding completion route in $M$ is the only completion-facing source available to a consumer.

The readback rows $W,R,A$ then bind finite observation windows, regular rational tolerance data, and the terminal Real seal to that same branch. The join row $J$ records that this branch-local route is the public coproduct-completion handoff.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for the excluded quotient, choice, host, or ambient-completeness objects, the stated rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Metric completion finite-coproduct universal route]
\label{thm:metric-completion-finite-coproduct-universal-route}
Every consumer that reads a finite coproduct after metric completion, or metric completion after a finite coproduct, factors through the displayed route
$$
\SumUp \longrightarrow \MetricCompletionUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp .
$$
The exported object is the branch classifier named by $I,S,M,W,R,A,J,H,C,P,N$, not a quotient-level universal property and not a selected completed representative.
\end{theorem}
\begin{proof}
Start with the finite index and coproduct rows $I,S$. They are the only rows that select a branch, so any universal read begins with the displayed finite case split.

For the chosen branch, project the corresponding $\MetricCompletionUp$ row from $M$. The carrier offers no completed branch outside this family.

Now pass through $W,R,A$. These rows provide the finite stream window, regular rational readback, and real seal used by the branch consumer.

Apply \autoref{thm:metric-completion-finite-coproduct-namecert-obligations}. The join, transport, replay, provenance, and naming rows keep the same route visible, so the consumer receives only the finite universal route and cannot import a quotient completion isomorphism or selected representative.
\end{proof}

\begin{theorem}[Metric completion finite-coproduct nonescape]
\label{thm:metric-completion-finite-coproduct-nonescape}
No accepted $\MetricCompletionFiniteCoproductUp$ consumer can escape from the finite branch route into quotient completion equality, selected limits, countable choice, an infinite coproduct, host-side case analysis, or ambient $\RealUp$ completeness. Every exposed claim is read through the same finite packet rows
$$
I,S,M,W,R,A,J,H,C,P,N .
$$
\end{theorem}
\begin{proof}
Use \autoref{thm:metric-completion-finite-coproduct-universal-route}. It places every completion-coproduct consumer behind the finite branch classifier and the branch-local completion rows.

The numerical boundary is fixed by $W,R,A$. These rows provide only finite windows, regular rational readback, and a Real seal for the displayed branch.

The support rows $J,H,C,P,N$ join, transport, replay, source, and name the same packet. Because no excluded object occurs as a coordinate of \autoref{def:metric-completion-finite-coproduct-carrier}, no consumer can export it.
\end{proof}

\closureat{MetricCompletionFiniteCoproductUp}{seedStr}

\begin{closurestatus}{\MetricCompletionFiniteCoproductUp}
  \constructivestory{A $\MetricCompletionFiniteCoproductUp$ packet is generated from a finite index row, a SumUp coproduct row, branchwise MetricCompletionUp rows, StreamName windows, RegSeqRat readback, a RealUp seal, a coproduct-completion join row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-finite-coproduct-carrier}, \autoref{thm:metric-completion-finite-coproduct-namecert-obligations}, \autoref{thm:metric-completion-finite-coproduct-universal-route}, and \autoref{thm:metric-completion-finite-coproduct-nonescape} seed the finite coproduct completion route over MetricCompletionUp, SumUp, StreamNameUp, RegSeqRatUp, RealUp, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, selected limits, countable choice, infinite coproducts, host case analysis, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite branch classification, branchwise completion routing, StreamName and RegSeqRat readback, Real seal exactness, nonescape, transport, replay, provenance, and local naming for BEDC.Derived.MetricCompletionFiniteCoproductUp.}
\end{closurestatus}
