\chapter{A Concrete Naming Certificate for $\MetricCompletionNaturalityUp$}
\label{ch:concrete-instances-metric-completion-naturality-namecert}
\origin{human}

Following Bishop and Bridges on constructive metric completion and uniform continuity, the $\MetricCompletionNaturalityUp$ packet records the finite L10 square by which a uniformly continuous source map is read by completion-facing consumers. It sits over the metric-completion surface of \autoref{ch:concrete-instances-metriccompletion-namecert}, the map carrier of \autoref{ch:concrete-instances-continuousmap-namecert}, the extension route of \autoref{ch:concrete-instances-uniform-continuous-extension-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only the displayed naturality packet; it is not a quotient completion construction, not a selected representative principle, not host function equality, not countable choice, and not ambient completeness of $\RealUp$.

\begin{definition}[Metric completion naturality carrier]
\label{def:metric-completion-naturality-carrier}
A $\MetricCompletionNaturalityUp$ carrier is a finite $\BHist$ packet
$$
N=(M_X,M_Y,F,E,S,R,A,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $M_X$ is the source $\MetricCompletionUp$ row, exposing the finite Cauchy-window requests inspected before the map is applied.
\item $M_Y$ is the target $\MetricCompletionUp$ row, exposing the completion-facing consumer reached after the map and extension rows have been displayed.
\item $F$ is the $\ContinuousMapUp$ row naming the displayed source map and the finite continuity data it exposes to the packet.
\item $E$ is the $\UniformContinuousExtensionUp$ row that transports the same displayed map through the completion interface.
\item $S$ is the $\StreamNameUp$ finite-window row shared by the source completion, target completion, and extension reads.
\item $R$ is the $\RegSeqRatUp$ readback row through which numerical tolerance requests are answered.
\item $A$ is the terminal $\RealUp$ seal row reached only after the stream window and regular readback rows have been fixed.
\item $H$ records componentwise $\hsame$ transport for the source completion, target completion, map, extension, stream-window, readback, real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the naturality route
$$
M_X \longmapsto F,E \longmapsto S,R,A \longmapsto M_Y .
$$
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionNaturalityUp$, $\MetricCompletionUp$, $\ContinuousMapUp$, $\UniformContinuousExtensionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\MetricCompletionNaturalityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M_X,M_Y,F,E,S,R,A,H,C,P,L$. It has no coordinate for quotient completion equality, selected representatives, host function equality, countable-choice schedules, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Metric completion naturality NameCert obligations]
\label{thm:metric-completion-naturality-namecert-obligations}
For every accepted $\MetricCompletionNaturalityUp$ carrier
$$
N=(M_X,M_Y,F,E,S,R,A,H,C,P,L),
$$
the local $\NameCert_{\MetricCompletionNaturalityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source completion, target completion, continuous-map, uniform-extension, stream-window, regular-readback, real-seal, transport, replay, provenance, and local naming rows;
\item source-before-extension exposure, requiring any completion-facing read to inspect $M_X$ and $F$ before the extension row $E$ can be consumed;
\item target-consumer routing, requiring $M_Y$ to be reached only after the displayed extension route has passed through $S,R,A$;
\item finite observation exactness, requiring the shared $\StreamNameUp$ and $\RegSeqRatUp$ rows to be the only numerical readback route between the extension row and the terminal $\RealUp$ seal;
\item classifier stability, requiring componentwise $\hsame$ transport through $H$ and displayed replay through $C$ to preserve the same finite naturality route;
\item ledger non-escape, excluding quotient completions, selected representatives, host function equality, countable choice, ambient $\RealUp$ completeness, Lean verification, and bridge checking from the packet.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:metric-completion-naturality-carrier}. The accepted packet displays exactly the two completion rows, the map row, the extension row, the finite observation rows, and the structural rows.

Source-before-extension exposure is read from $M_X,F,E$. The map row $F$ is available only with the source completion observations in $M_X$, and the extension row $E$ records the completion-facing transport of that same displayed map.

Target-consumer routing is read from $M_Y$ together with $S,R,A$. The target completion row can be offered to a consumer only after the extension has exposed the finite stream windows, regular readback, and real seal used by the route.

Classifier stability is componentwise transport through $H$ followed by replay through $C$. Since $P$ and $L$ only source and name the same displayed route, there is no separate row from which quotient completion equality, selected representatives, host function equality, choice, ambient completeness, Lean verification, or bridge credentials could be projected.
\end{proof}

\begin{theorem}[Metric completion naturality consumer nonescape]
\label{thm:metric-completion-naturality-consumer-nonescape}
Every completion-facing or real-seal-facing consumer of an accepted $\MetricCompletionNaturalityUp$ carrier
$$
N=(M_X,M_Y,F,E,S,R,A,H,C,P,L)
$$
must factor through the finite route
$$
M_X,F \longmapsto E \longmapsto S,R,A \longmapsto M_Y \longmapsto H,C,P,L .
$$
Consequently the consumer receives only the displayed source completion row, continuous-map row, uniform-extension row, shared finite window, regular readback, terminal real seal, target completion row, transport, replay, provenance, and local name. It exports no quotient completion, no selected representative, no host function equality, no countable-choice schedule, no ambient $\RealUp$ completeness theorem, and no bridge-checking credential.
\end{theorem}
\begin{proof}
Start with a completion-facing or real-seal-facing read of the carrier. Projection first exposes the source completion row $M_X$ and the continuous-map row $F$, so the consumer cannot begin from a hidden completed representative or a host function.

The extension row $E$ is then the only row carrying the displayed map through the completion interface. It does not add a quotient completion object; it only names the finite extension route attached to the same source and map rows.

The read next passes through $S,R,A$. These rows fix the finite observation windows, the regular rational readback, and the terminal real seal before the target completion row $M_Y$ is available.

Finally $H,C,P,L$ transport, replay, source, and name the same displayed route. Because the carrier has no further coordinates, the stated excluded principles cannot be exported by any consumer of the packet.
\end{proof}

\closureat{MetricCompletionNaturalityUp}{seedStr}

\begin{closurestatus}{\MetricCompletionNaturalityUp}
  \constructivestory{A $\MetricCompletionNaturalityUp$ packet is generated from source and target MetricCompletion rows, a ContinuousMap row, a UniformContinuousExtension row, shared StreamName windows, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-naturality-carrier}, \autoref{thm:metric-completion-naturality-namecert-obligations}, and \autoref{thm:metric-completion-naturality-consumer-nonescape} seed the finite naturality route from source metric completion through displayed continuous-map extension to target completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host function equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-before-extension exposure, target-consumer routing, finite observation exactness, classifier stability, consumer nonescape, and a Lean carrier/obligation formalization for BEDC.Derived.MetricCompletionNaturalityUp.}
\end{closurestatus}
