\chapter{A Concrete Naming Certificate for $\LocatedCompletionFunctorUp$}
\label{ch:concrete-instances-located-completion-functor-namecert}
\origin{human}

Following Bishop and Bridges on located constructive metric completions and Kelley on functorial completion discipline, the $\LocatedCompletionFunctorUp$ packet records the finite route by which a located metric-space presentation is sent to its completion-facing regular-name surface. It sits after the located real boundary of \autoref{ch:concrete-instances-located-real-namecert}, the metric-completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the universal-property witness of \autoref{ch:concrete-instances-cauchy-completion-universal-property-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the displayed functorial handoff used by L10 completion consumers; it is not a quotient completion theorem, not a selected host limit, not countable choice, and not ambient $\RealUp$ completeness.

\begin{definition}[Located completion functor carrier]
\label{def:located-completion-functor-carrier}
A $\LocatedCompletionFunctorUp$ carrier is a finite $\BHist$ packet
$$
\mathsf{LocatedCompletionFunctor}(L,M,U,R,E,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LocatedRealUp$ or located metric-source row exposing the positive-apartness and approximation data that make Cauchy requests decidable as finite located reads.
\item $M$ is the $\MetricCompletionUp$ carrier row naming the completion-facing object surface, without quotienting Cauchy names.
\item $U$ is the $\CauchyCompletionUniversalPropertyUp$ row recording the displayed universal-property handoff for uniformly continuous maps already routed through finite data.
\item $R$ is the $\RegSeqRatUp$ readback row used when the completion object is presented through regular rational names.
\item $E$ is the terminal $\RealUp$ seal row reached only after the located, completion, universal-property, and regular rational rows have been displayed.
\item $F$ is the functorial action row, naming how source maps are transported to completion-facing maps through $L,M,U,R,E$.
\item $H$ records componentwise $\hsame$ transport for the located source, completion carrier, universal-property handoff, regular rational readback, Real seal, functorial action, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located source request through the completion, universal-property, regular rational, Real-seal, and functorial-action rows.
\item $P$ is the $\Pkg$ provenance over $\LocatedCompletionFunctorUp$, $\LocatedRealUp$, $\MetricCompletionUp$, $\CauchyCompletionUniversalPropertyUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCompletionFunctorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,M,U,R,E,F,H,C,P,N$. It has no coordinate for quotient completion equality, selected limits, countable-choice schedules, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge data.
\end{definition}

\begin{theorem}[Located completion functor NameCert obligations]
\label{thm:located-completion-functor-namecert-obligations}
For every accepted $\LocatedCompletionFunctorUp$ carrier $\mathsf{LocatedCompletionFunctor}(L,M,U,R,E,F,H,C,P,N)$, the local $\NameCert_{\LocatedCompletionFunctorUp}$ surface consists exactly of carrier admission for the located source, metric-completion carrier, Cauchy-completion universal-property handoff, regular rational readback, Real seal, functorial action, componentwise transport, displayed replay, provenance, and local naming rows.

Every completion-facing consumer must read the route
$$
L,M,U,R,E,F,H,C,P,N
$$
before treating a located map as a completion map. The route exports no quotient completion theorem, selected host limit, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge datum.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-completion-functor-carrier}. The accepted tuple displays the located source row, completion carrier, universal-property row, regular rational readback, Real seal, functorial action, and structural support.

The completion-facing read begins with $L$ and $M$. These rows expose located input data and the completion object surface before any map action is available.

Next read $U,R,E,F$. The universal-property row supplies the finite handoff discipline, the regular rational and Real rows name the target readback boundary, and the functorial action row records the transported map only after those rows are present.

Finally $H,C,P,N$ preserve, replay, source, and name the same finite route. Since no quotient equality, selected limit, choice schedule, trichotomy row, host real equality, Real completeness theorem, Lean verification row, or bridge datum is present in the carrier, none can become a local NameCert obligation.
\end{proof}

\begin{theorem}[Located completion functor Real handoff]
\label{thm:located-completion-functor-real-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\LocatedCompletionFunctorUp$ packet reaches the Real-facing handoff only through the displayed located source row, metric-completion row, Cauchy-completion universal-property row, regular rational readback row, Real seal row, and functorial-action row of \autoref{def:located-completion-functor-carrier}. In particular, the handoff is a finite NameCert route for located completion data, not a quotient completion, selected host limit, countable-choice construction, trichotomy principle, host real equality, or ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Start with a $\RegSeqRatUp$ or $\RealUp$ consumer. The consumer-facing evidence is the displayed carrier, so the located source, completion object, universal-property handoff, readback, seal, and functorial action are the only rows it may inspect.

The regular rational and Real rows are downstream. The consumer reaches $R$ and $E$ only after $L,M,U$ have fixed the located completion route and before $F$ packages the transported map.

The support rows $H,C,P,N$ carry the same route through transport, replay, provenance, and local naming. No coordinate supplies quotient completion equality, a selected limit, countable choice, trichotomy, host equality, ambient Real completeness, Lean verification, or bridge checking.
\end{proof}

\falsifiablePrediction{Every accepted $\LocatedCompletionFunctorUp$ packet factors a Real-facing completion read through one located source row, one MetricCompletion row, one CauchyCompletionUniversalProperty handoff, one RegSeqRat readback, one RealUp seal, one functorial-action row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{located-real, metric-completion, cauchy-completion-universal-property, regseqrat, real: $\LocatedCompletionFunctorUp$ is not bijective to any listed sibling because it jointly carries the located source, completion carrier, universal-property handoff, regular rational readback, Real seal, and functorial action as one certificate.}

\closureat{LocatedCompletionFunctorUp}{seedStr}

\begin{closurestatus}{\LocatedCompletionFunctorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-completion-functor-carrier}, \autoref{thm:located-completion-functor-namecert-obligations}, and \autoref{thm:located-completion-functor-real-handoff} seed the finite located-completion functor route over located source rows, metric-completion carriers, universal-property handoffs, regular rational readback, Real seals, functorial action, and local NameCert data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-source exactness, completion-carrier handoff, universal-property consumption, RegSeqRat and Real handoff, functorial-action exactness, transport, replay, provenance, and local naming for BEDC.Derived.LocatedCompletionFunctorUp.}
  \constructivestory{A $\LocatedCompletionFunctorUp$ packet is generated from a located source row, a MetricCompletion row, a CauchyCompletionUniversalProperty handoff, a RegSeqRat readback row, a RealUp seal row, a functorial-action row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
