\chapter{A Concrete Naming Certificate for $\StieltjesMeasureBoundaryUp$}
\label{ch:concrete-instances-stieltjes-measure-boundary-namecert}
\origin{human}

Following Stieltjes, Jordan, and the Bishop--Bridges constructive reading of bounded variation, this packet records only the finite boundary by which a $\BoundedVariationUp$ integrator supplies interval-jump rows to $\RiemannStieltjesUp$ and $\RegulatedCauchyIntegralUp$ consumers. It sits after the partition-variation ledger of \autoref{ch:concrete-instances-boundedvariation-namecert}, the tagged-sum handoff of \autoref{ch:concrete-instances-riemannstieltjes-namecert}, the regulated Cauchy readback of \autoref{ch:concrete-instances-regulated-cauchy-integral-namecert}, the regular rational surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic endpoint core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite interval-jump boundary; it is not a variation measure, a Lebesgue integration object, a quotient of host functions, a selected limit, countable choice, or an ambient $\RealUp$ completeness principle.

\begin{definition}[Stieltjes measure boundary carrier]
\label{def:stieltjes-measure-boundary-carrier}
A $\StieltjesMeasureBoundaryUp$ carrier is a finite $\BHist$ packet
$$
S=(B,\Pi,J,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BoundedVariationUp$ source row naming the integrator only through displayed finite partition-variation data.
\item $\Pi$ is the displayed interval partition, including ordered endpoints, interval cells, and the refinement witnesses on which boundary reads are requested.
\item $J$ is the endpoint-jump $\DyadicRatCoreUp$ ledger, recording the finite left and right endpoint differences attached to the cells of $\Pi$.
\item $R$ is the $\RegSeqRatUp$ readback row that exposes those jump rows at the requested rational windows.
\item $E$ is the terminal $\RealUp$ seal reached only after $B,\Pi,J,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the bounded-variation source, partition, jump ledger, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from bounded-variation partition reads to interval jumps, from jumps to regular rational readback, and from readback to the $\RealUp$ seal.
\item $P$ is the $\Pkg$ provenance over $\StieltjesMeasureBoundaryUp$, $\BoundedVariationUp$, $\RiemannStieltjesUp$, $\RegulatedCauchyIntegralUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StieltjesMeasureBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,\Pi,J,R,E,H,C,P,N$. It has no coordinate for measure completion, Lebesgue integration, a host function quotient, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Stieltjes measure boundary NameCert obligations]
\label{thm:stieltjes-measure-boundary-namecert-obligations}
For every accepted $\StieltjesMeasureBoundaryUp$ carrier
$$
S=(B,\Pi,J,R,E,H,C,P,N),
$$
the local $\NameCert_{\StieltjesMeasureBoundaryUp}$ surface consists exactly of carrier admission for the $\BoundedVariationUp$ source, displayed interval-partition exposure through $\Pi$, endpoint-jump exactness through the $\DyadicRatCoreUp$ ledger $J$, $\RegSeqRatUp$ readback through $R$, terminal $\RealUp$ sealing through $E$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:stieltjes-measure-boundary-carrier}. The source row $B$ is already the finite partition-variation object of \autoref{ch:concrete-instances-boundedvariation-namecert}, so the boundary packet begins from displayed partition data rather than from a completed variation measure.

The interval and jump obligations are the rows $\Pi$ and $J$. The partition cells provide the only endpoint pairs that may be inspected, and the dyadic ledger records the corresponding finite endpoint differences through \autoref{ch:concrete-instances-dyadicratcore-namecert}.

The readback and seal obligations are downstream. The regular rational route of \autoref{ch:concrete-instances-regseqrat-namecert} consumes $J$ through $R$, and the real-name route of \autoref{ch:concrete-instances-real-namecert} consumes $R$ through $E$. Transport, replay, provenance, and local naming are exactly $H,C,P,N$, leaving no hidden measure, quotient, choice, selected-limit, or completeness row.
\end{proof}

\begin{theorem}[Stieltjes boundary bounded-variation handoff]
\label{thm:stieltjes-measure-boundary-bounded-variation-handoff}
Every $\RiemannStieltjesUp$ or $\RegulatedCauchyIntegralUp$ consumer of an accepted $\StieltjesMeasureBoundaryUp$ packet receives the integrator boundary only through the displayed route
$$
\BoundedVariationUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert_{\StieltjesMeasureBoundaryUp}.
$$
Concretely, the consumer must read the bounded-variation source $B$, the interval partition $\Pi$, the endpoint-jump ledger $J$, and the regular rational readback $R$ before any $\RealUp$ seal $E$ is visible.
\end{theorem}
\begin{proof}
Start with the bounded-variation source. By \autoref{ch:concrete-instances-boundedvariation-namecert}, that source exposes partition data and dyadic variation ledgers, not a variation measure or a host function quotient.

The boundary carrier refines the source to endpoint jumps on the displayed partition. The cells of $\Pi$ determine the finite list of endpoint pairs, and the ledger $J$ records their dyadic jump reads.

Now pass to consumers. The $\RiemannStieltjesUp$ route of \autoref{ch:concrete-instances-riemannstieltjes-namecert} and the $\RegulatedCauchyIntegralUp$ route of \autoref{ch:concrete-instances-regulated-cauchy-integral-namecert} may consume only the displayed regular readback and seal rows $R,E$ together with $H,C,P,N$. Thus the handoff is the listed finite route, with no channel for measure completion, Lebesgue integration, selected limits, countable choice, or ambient real completeness.
\end{proof}

\begin{theorem}[Stieltjes boundary Real seal non-escape]
\label{thm:stieltjes-measure-boundary-real-seal-nonescape}
The $\RealUp$ seal of an accepted $\StieltjesMeasureBoundaryUp$ carrier is available only after the bounded-variation source row, displayed interval partition, endpoint-jump $\DyadicRatCoreUp$ ledger, and $\RegSeqRatUp$ readback have been read. The seal exposes the same finite interval-jump boundary and exports no measure completion, Lebesgue integration object, host function quotient, selected limit, countable-choice schedule, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Project the seal coordinate of \autoref{def:stieltjes-measure-boundary-carrier}. The row $E$ is downstream from $B,\Pi,J,R$ and is transported or replayed only by the structural rows $H$ and $C$.

Apply \autoref{thm:stieltjes-measure-boundary-namecert-obligations}. It identifies the bounded-variation source, partition exposure, dyadic jump ledger, regular readback, Real seal, transport, replay, provenance, and local naming rows as the complete local certificate surface.

Apply \autoref{thm:stieltjes-measure-boundary-bounded-variation-handoff}. Every integration-facing read must pass through the same finite jump route before the seal is visible. Since none of the excluded objects is a carrier coordinate, the $\RealUp$ seal cannot export them.
\end{proof}

\closureat{StieltjesMeasureBoundaryUp}{seedStr}

\begin{closurestatus}{\StieltjesMeasureBoundaryUp}
  \constructivestory{A $\StieltjesMeasureBoundaryUp$ packet is generated from a BoundedVariation source row, a displayed interval partition, endpoint-jump DyadicRatCore ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stieltjes-measure-boundary-carrier}, \autoref{thm:stieltjes-measure-boundary-namecert-obligations}, \autoref{thm:stieltjes-measure-boundary-bounded-variation-handoff}, and \autoref{thm:stieltjes-measure-boundary-real-seal-nonescape} seed the finite Stieltjes boundary by which bounded-variation interval jumps are read by Riemann--Stieltjes and regulated Cauchy integral consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim measure completion, Lebesgue integration, host function quotients, selected limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint-jump exactness, regular readback, bounded-variation handoff, Real-seal non-escape, transport and replay stability, provenance non-escape, and a Lean carrier/obligation formalization for BEDC.Derived.StieltjesMeasureBoundaryUp.}
\end{closurestatus}
