\chapter{A Concrete Naming Certificate for $\LocatedHeineBorelSubcoverUp$}
\label{ch:concrete-instances-located-heine-borel-subcover-namecert}
\origin{human}

Following Bishop and Bridges' constructive finite-subcover treatment for compact intervals, the $\LocatedHeineBorelSubcoverUp$ packet records the BEDC route that turns a located closed interval cover request into a displayed finite subcover through finite nets and positive-radius data. It sits over the located interval finite-net surface of \autoref{ch:concrete-instances-located-closed-interval-finite-net-namecert}, the compact-cover radius route of \autoref{ch:concrete-instances-lebesgue-number-lemma-namecert}, the finite-net interval-cover packet of \autoref{ch:concrete-instances-heine-borel-finite-net-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet names a located finite-subcover certificate; it does not claim unrestricted open-cover Heine--Borel compactness, selected subcovers from arbitrary covers, countable choice, quotient interval equality, or ambient $\RealUp$ completeness.

\begin{definition}[Located Heine--Borel subcover carrier]
\label{def:located-heine-borel-subcover-carrier}
A $\LocatedHeineBorelSubcoverUp$ carrier is a finite $\BHist$ packet
$$
S=(I,F,L,H,R,D,E,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the located closed interval source row, exposing endpoint names, endpoint order, and locatedness only as finite $\RealUp$ histories.
\item $F$ is the $\LocatedClosedIntervalFiniteNetUp$ finite-net row, listing the mesh scale and finite interval net used by the cover request.
\item $L$ is the $\LebesgueNumberLemmaUp$ positive-radius row attached to the displayed finite cover or pointwise radius family.
\item $H$ is the $\HeineBorelFiniteNetUp$ sibling row that records the finite-net interval-cover route over the same interval, net, radius, dyadic, and real-seal data.
\item $R$ is the retained-subcover row, listing exactly the finitely many cover witnesses selected by the displayed net and radius checks.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording mesh width, radius slack, endpoint containment, and finite neighborhood comparisons.
\item $E$ is the terminal $\RealUp$ seal row for endpoint, radius, and coverage reads.
\item $T$ records componentwise $\hsame$ transport for the interval source, finite-net row, radius row, finite-net sibling row, retained-subcover row, dyadic ledger, real seal, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from a located cover request through $I,F,L,H,R,D,E,T,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedHeineBorelSubcoverUp$, $\LocatedClosedIntervalFiniteNetUp$, $\LebesgueNumberLemmaUp$, $\HeineBorelFiniteNetUp$, $\RealUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedHeineBorelSubcoverUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,F,L,H,R,D,E,T,C,P,N$. It has no coordinate for arbitrary open covers, unrestricted Heine--Borel compactness, selected subcover functionals, quotient interval representatives, countable choice, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located Heine--Borel subcover NameCert obligations]
\label{thm:located-heine-borel-subcover-namecert-obligations}
For every accepted $\LocatedHeineBorelSubcoverUp$ carrier
$$
S=(I,F,L,H,R,D,E,T,C,P,N),
$$
the local $\NameCert_{\LocatedHeineBorelSubcoverUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the located interval source, finite-net row, positive-radius row, finite-net sibling row, retained-subcover row, dyadic ledger, real seal, transport, replay, provenance, and local naming rows;
\item located interval exposure, requiring every cover request to display $I$ and the finite-net row $F$ before any retained cover witness is inspected;
\item radius compatibility, requiring $L$ and $D$ to record the positive-radius and dyadic slack checks that allow listed net points to control nearby interval points;
\item finite-subcover exactness, requiring $R$ to list only cover witnesses reached through the finite net, radius ledger, and $\HeineBorelFiniteNetUp$ sibling route;
\item real-seal non-escape, requiring $E$ to be downstream of the located interval, finite-net, radius, retained-subcover, and dyadic rows;
\item structural preservation through $T,C,P,N$ and refusal of arbitrary open-cover compactness, unrestricted Heine--Borel, selected subcover functionals, quotient interval representatives, countable choice, host real equality, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
No located finite-subcover obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-heine-borel-subcover-carrier}. The analytic rows are exactly the located interval source $I$, finite-net row $F$, positive-radius row $L$, finite-net sibling row $H$, retained-subcover row $R$, dyadic ledger $D$, and terminal real seal $E$.

The cover request first exposes $I$ and $F$. The packet therefore reads a located interval and a displayed finite net before it can inspect any cover witness, so the route cannot start from an arbitrary open-cover selector.

The radius step is finite. The row $L$ supplies the positive radius ledger, while $D$ records the mesh-width and endpoint-slack comparisons that transfer a witness at a listed net point to nearby interval points.

The retained row $R$ is downstream of $F,L,H,D$. Hence every retained cover witness is tied to the same finite-net route already named by \autoref{ch:concrete-instances-heine-borel-finite-net-namecert}, and the terminal seal $E$ is reached only after those finite checks have been displayed.

Transport, replay, provenance, and local naming preserve this finite surface. Since the refused objects have no carrier coordinate, the local certificate exports only the located finite-subcover route.
\end{proof}

\begin{theorem}[Located Heine--Borel finite-net route]
\label{thm:located-heine-borel-subcover-finite-net-route}
Every located cover read from an accepted $\LocatedHeineBorelSubcoverUp$ packet factors through the finite route
$$
\LocatedClosedIntervalFiniteNetUp \longmapsto \LebesgueNumberLemmaUp \longmapsto \HeineBorelFiniteNetUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp .
$$
The exported object is the retained finite subcover row $R$ over $I,F,L,H,D,E,T,C,P,N$, not an unrestricted open-cover Heine--Borel principle.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $S=(I,F,L,H,R,D,E,T,C,P,N)$. The located interval and finite net are exposed by $I$ and $F$, the positive-radius ledger is $L$, and the already displayed finite-net cover route is $H$.

The retained-subcover row $R$ may be read only after those rows. Its witnesses are checked by the dyadic ledger $D$ and then sealed by $E$, so the exported finite subcover is a displayed BEDC packet row rather than a host-level choice operation.

Replay through $C$, transport through $T$, provenance through $P$, and naming through $N$ keep the same route. No arbitrary open cover, unrestricted compactness theorem, quotient interval representative, countable-choice row, or ambient completeness coordinate is available to bypass it.
\end{proof}

\closureat{LocatedHeineBorelSubcoverUp}{seedStr}

\begin{closurestatus}{\LocatedHeineBorelSubcoverUp}
  \constructivestory{A $\LocatedHeineBorelSubcoverUp$ packet is generated from a located closed interval source, a LocatedClosedIntervalFiniteNet row, a LebesgueNumberLemma positive-radius ledger, a HeineBorelFiniteNet sibling row, retained finite subcover witnesses, a DyadicRatCore tolerance ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-heine-borel-subcover-carrier}, \autoref{thm:located-heine-borel-subcover-namecert-obligations}, and \autoref{thm:located-heine-borel-subcover-finite-net-route} seed the located finite-subcover route over interval nets, positive-radius ledgers, finite-net cover rows, dyadic tolerances, and Real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close unrestricted open-cover Heine--Borel compactness, arbitrary subcover selection, countable choice, quotient interval equality, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located interval exposure, radius compatibility, finite-subcover exactness, real-seal non-escape, transport, replay, provenance, and local naming for BEDC.Derived.LocatedHeineBorelSubcoverUp.}
\end{closurestatus}
