\chapter{A Concrete Naming Certificate for $\CauchyProductMetricUp$}
\label{ch:concrete-instances-cauchy-product-metric-namecert}
\origin{human}

Following Bishop--Bridges on metric products and regular Cauchy names, the $\CauchyProductMetricUp$ packet records the finite product-metric surface used by two displayed CauchyProduct rows before any host product metric or Real completeness principle is available. It sits beside the product route of \autoref{ch:concrete-instances-cauchyproduct-namecert}, the metric carrier surface of \autoref{ch:concrete-instances-metric-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the scheduled window layer of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives downstream Real, metric, and Cauchy-completion consumers a non-quotient product-distance certificate over displayed rows only.

\begin{definition}[CauchyProductMetric carrier]
\label{def:cauchy-product-metric-carrier}
A $\CauchyProductMetricUp$ carrier is a finite $\BHist$ packet
$$
M=(L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ and $R$ are the two accepted $\CauchyProductUp$ source rows. Each row supplies a finite product-name route rather than host product equality.
\item $W_L$ and $W_R$ are the paired $\StreamNameUp$ window rows inspected on the left and right product names.
\item $Q_L$ and $Q_R$ are the $\RegSeqRatUp$ readback rows attached to the two displayed window pairs.
\item $D$ is the $\DyadicRatCoreUp$ product-distance ledger. It records coordinate tolerances, the product-distance radius, the comparison budget, and the displayed error allowance used by the packet.
\item $\Delta$ is the $\MetricUp$ distance row, read only through the displayed product windows, regular rational readbacks, and dyadic ledger.
\item $E$ is the terminal $\RealUp$ seal for the product-distance read.
\item $H$ records componentwise $\hsame$ transport for the CauchyProduct rows, stream windows, regular readbacks, dyadic ledger, metric row, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a product-metric request through $L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E$.
\item $P$ is the $\Pkg$ provenance over $\CauchyProductMetricUp$, $\CauchyProductUp$, $\MetricUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyProductMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E,H,C,P,N$. It has no coordinate for host product metrics, quotient stream equality, selected product limits, trichotomy, detached real carriers, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.CauchyProductMetricUp.CauchyProductMetricTasteGate\_single\_carrier\_alignment}

\begin{theorem}[CauchyProductMetric NameCert obligations]
\label{thm:cauchy-product-metric-namecert-obligations}
For every accepted $\CauchyProductMetricUp$ carrier $M=(L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E,H,C,P,N)$, the local $\NameCert_{\CauchyProductMetricUp}$ surface consists exactly of carrier admission for the two $\CauchyProductUp$ rows, paired $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ product-distance ledger, $\MetricUp$ distance row, $\RealUp$ seal, componentwise transport, displayed continuation replay, package provenance, local naming, and refusal of host product metrics, quotient stream equality, selected product limits, trichotomy, detached real carriers, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-product-metric-carrier}. The accepted packet exposes exactly the two CauchyProduct rows, paired stream windows, regular rational readbacks, dyadic product-distance ledger, metric row, Real seal, and structural rows.

The product-distance ledger is downstream of the displayed windows and readbacks. Thus $D$ cannot be read before $W_L,W_R,Q_L,Q_R$ have fixed the finite CauchyProduct observations.

The metric and Real rows are then forced through $\Delta$ and $E$. The distance row reads only the displayed dyadic ledger, and the seal row records the resulting product-distance value without adding a second carrier.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for host product metrics, quotient stream equality, selected limits, trichotomy, detached real carriers, or ambient completeness, the listed obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[CauchyProductMetric projection stability]
\label{thm:cauchy-product-metric-projection-stability}
Let $M=(L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E,H,C,P,N)$ be an accepted $\CauchyProductMetricUp$ packet. Any projection-facing metric consumer that reads the left or right coordinate distance must factor through the same $\CauchyProductUp$ source row, the same $\StreamNameUp$ window row, the same $\RegSeqRatUp$ readback row, the shared $\DyadicRatCoreUp$ product-distance ledger, and the same structural rows $H,C,P,N$. Projection reads may forget the unused coordinate, but they cannot introduce a host product metric, a quotient stream, a selected limit, or an independent real carrier.
\end{theorem}
\begin{proof}
Start with a projection-facing read of the accepted packet. The only coordinate data exposed by the carrier are $L,R$ together with their displayed window and regular readback rows.

For the left projection, the read passes through $L,W_L,Q_L$ and then through the shared dyadic ledger $D$. For the right projection, the same argument uses $R,W_R,Q_R$ and the same ledger.

The metric row $\Delta$ and Real seal $E$ are downstream of this ledger. Forgetting one coordinate therefore removes data from the displayed packet, but it does not create a new metric source or a new Real-facing endpoint.

The structural rows $H,C,P,N$ preserve exactly this projected route. The omitted coordinates in \autoref{def:cauchy-product-metric-carrier} rule out host product metrics, quotient streams, selected limits, and detached real carriers.
\end{proof}

\begin{theorem}[CauchyProductMetric Real seal boundary]
\label{thm:cauchy-product-metric-real-seal-boundary}
Every $\RealUp$ consumer of an accepted $\CauchyProductMetricUp$ packet must first display the finite route
$$
\CauchyProductUp,\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp,\MetricUp,\RealUp
$$
through the rows $L,R,W_L,W_R,Q_L,Q_R,D,\Delta,E,H,C,P,N$. The Real seal is a product-distance seal for this displayed route only; it exports no host product metric, no quotient product of Cauchy streams, no selected product limit, no trichotomy row, no detached real carrier, and no ambient completeness witness.
\end{theorem}
\begin{proof}
Begin with a Real-facing read. Carrier admission makes the two CauchyProduct rows visible, but no Real seal is available before the paired stream windows and regular readbacks have been displayed.

The dyadic ledger $D$ records the product-distance budget attached to those windows. The metric row $\Delta$ can only read this ledger, so it cannot import a host product metric or a separate distance object.

The seal $E$ is reached after $\Delta$, and the continuation row $C$ replays the same route for downstream Real, metric, or completion-facing consumers. The transport and provenance rows keep the endpoint tied to $L,R,W_L,W_R,Q_L,Q_R,D,\Delta$.

Thus the consumer receives exactly the finite product-distance route named by the local certificate. All quotient, selection, trichotomy, detached-carrier, host-metric, and ambient-completeness exits are outside the packet.
\end{proof}

\closureat{CauchyProductMetricUp}{seedStr}

\begin{closurestatus}{\CauchyProductMetricUp}
  \constructivestory{A $\CauchyProductMetricUp$ packet is generated from two CauchyProduct source rows, paired StreamName windows, RegSeqRat readbacks, a DyadicRatCore product-distance ledger, a MetricUp distance row, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-product-metric-carrier}, \autoref{thm:cauchy-product-metric-namecert-obligations}, \autoref{thm:cauchy-product-metric-projection-stability}, and \autoref{thm:cauchy-product-metric-real-seal-boundary} seed the finite product-metric route from CauchyProduct rows through displayed windows, regular readbacks, dyadic product-distance ledgers, metric rows, and Real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host product metrics, quotient stream equality, selected product limits, trichotomy, detached real carriers, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, product-distance ledger exactness, projection stability, Real seal boundary, transport, replay, provenance, and local naming for BEDC.Derived.CauchyProductMetricUp.}
\end{closurestatus}
