\chapter{A Concrete Naming Certificate for $\AlexanderDualTriggerAlgebraUp$}
\label{ch:concrete-instances-alexander-dual-trigger-algebra-namecert}
\origin{ai}

The $\AlexanderDualTriggerAlgebraUp$ packet realizes the Alexander-dual trigger and blocker algebra of \autoref{subsec:philosophy-dna-window-six-boundary-tiles} as finite BEDC NameCert data. It sits over the finite $\BoolUp$ tag discipline of \autoref{ch:concrete-instances-bool-namecert}, the finite observation interface of \autoref{ch:concrete-instances-finite-observation-interface-namecert}, the DNA boundary-tile carrier of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the six-tile coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the boundary-trigger closure packet of \autoref{ch:concrete-instances-dna-boundary-trigger-closure-namecert}, and the finite coverage-trigger algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}. The packet names the blocker-dual surface as finite rows; it is not a polynomial-ring oracle, stochastic biological model, quotient codon semantics, infinite trigger search, or hidden Alexander-duality principle.

\begin{definition}[AlexanderDualTriggerAlgebra carrier]
\label{def:alexander-dual-trigger-algebra-carrier}
An $\AlexanderDualTriggerAlgebraUp$ carrier is a finite $\BHist$ packet
$$
A=(B,T,I,U,L,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the boundary-tile carrier row read through $\DnaWindowSixBoundaryTileUp$ and $\SixBoundaryTileCoverageUp$.
\item $T$ is the trigger row recording the finite coordinate supports whose full-trigger behavior is visible.
\item $I$ is the inactive-face row recording the complements that remain blocked by a missed coordinate.
\item $U$ is the blocker-dual cover row, carrying the four displayed dual generator faces and their finite lcm-degree ledger.
\item $L$ is the $\BoolUp$ and finite-observation ledger that tags present, absent, trigger, blocker, active, and inactive faces without importing host truth values.
\item $R$ is the transport row from boundary tiles through $\DnaBoundaryTriggerClosureUp$ and $\WindowCoverageTriggerAlgebraUp$ to the displayed blocker-dual cover.
\item $H$ records componentwise $\hsame$ transport for boundary tiles, trigger rows, inactive faces, blocker-dual cover rows, finite tags, algebra transport, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from each dual-trigger read through $B,T,I,U,L,R,H$.
\item $P$ is the $\Pkg$ provenance over $\AlexanderDualTriggerAlgebraUp$, $\BoolUp$, $\FiniteObservationInterfaceUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\DnaBoundaryTriggerClosureUp$, $\WindowCoverageTriggerAlgebraUp$, the Alexander-dual trigger source vision, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AlexanderDualTriggerAlgebraUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,T,I,U,L,R,H,C,P,N$. It has no coordinate for host polynomial equality, ambient monomial ideals, stochastic evolutionary dynamics, quotient codon equality, infinite trigger search, or a hidden duality oracle.
\end{definition}

\begin{theorem}[AlexanderDualTriggerAlgebra NameCert obligations]
\label{thm:alexander-dual-trigger-algebra-namecert-obligations}
For every accepted $\AlexanderDualTriggerAlgebraUp$ carrier $A=(B,T,I,U,L,R,H,C,P,N)$, the local $\NameCert_{\AlexanderDualTriggerAlgebraUp}$ surface consists exactly of boundary-tile admission, trigger-row exposure, inactive-face exposure, blocker-dual cover exactness, finite Bool and observation tagging, algebra transport, componentwise transport, displayed replay, provenance, and local naming.

The blocker-dual cover row $U$ is accepted only when its trigger and blocker faces are read through the displayed $B,T,I,L,R$ route. Any consumer that attempts to read Alexander-dual data without those rows, or that replaces them by host polynomial equality, an ambient ideal, quotient codon semantics, stochastic dynamics, infinite search, or a hidden duality oracle, leaves the accepted packet surface.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:alexander-dual-trigger-algebra-carrier}. The rows $B,T,I,U,L,R$ expose the boundary-tile source, trigger supports, inactive faces, blocker-dual cover, finite tag ledger, and transport from the boundary-trigger algebra.

The cover row is finite. It records only the four displayed dual generator faces and their lcm-degree ledger, with $\BoolUp$ and finite-observation rows marking which faces are present, absent, active, inactive, triggering, or blocking.

Finally $H,C,P,N$ preserve the same displayed route. Since no host polynomial equality, ambient ideal, stochastic model, quotient codon equality, infinite search, or hidden duality oracle is a carrier coordinate, the local NameCert obligations are exactly the listed finite rows.
\end{proof}

\begin{theorem}[AlexanderDualTriggerAlgebra blocker-duality nonescape]
\label{thm:alexander-dual-trigger-algebra-blocker-duality-nonescape}
Every accepted $\AlexanderDualTriggerAlgebraUp$ read factors through displayed trigger, blocker, inactive-face, dual-cover, transport, replay, provenance, and local $\NameCert$ rows:
$$
B,T,I,U,L,R,H,C,P,N.
$$
In particular, a dual-trigger consumer cannot replace the blocker-duality row by the $\BoolUp$ tag discipline alone, by finite observation alone, by boundary closure alone, by trigger-hypergraph reliability alone, by universal coverage-trigger algebra alone, or by any host polynomial-ring equality.
\end{theorem}
\begin{proof}
Read the boundary source first. The row $B$ supplies the boundary tiles and coverage rows, while $T$ and $I$ separate visible trigger supports from inactive faces.

Next read the blocker-dual data. The row $U$ carries the dual-cover faces, and $L$ records the finite Bool and observation tags needed to distinguish trigger, blocker, active, and inactive positions.

The algebra transport $R$ then ties those rows to the boundary-trigger closure and coverage-trigger algebra siblings. The structural rows $H,C,P,N$ preserve the same route, so no sibling alone can absorb the blocker-duality coordinate and no host polynomial equality can be exported.
\end{proof}

\falsifiablePrediction{Every accepted $\AlexanderDualTriggerAlgebraUp$ read factors through displayed trigger, blocker, inactive-face, dual-cover, transport, replay, provenance, and local $\NameCert$ rows; omitting any of those rows refutes the packet.}

\independenceWitness{bool, finite-observation-budget-selector, dna-boundary-trigger-closure, trigger-hypergraph-reliability, universal-coverage-trigger-algebra: no listed sibling is bijective with $\AlexanderDualTriggerAlgebraUp$ because the packet jointly carries trigger rows, blocker rows, inactive-face rows, dual-cover rows, finite tag ledgers, algebra transport, replay, provenance, and local naming. A bijection preserving only finite tags, observation budgets, boundary closure, reliability, or coverage-trigger closure cannot preserve the blocker-duality row $U$ together with the inactive-face row $I$.}

The Lean follow-up \texttt{BEDC.Derived.AlexanderDualTriggerAlgebraUp.TasteGate} supplies explicit $\Nontrivial\ \AlexanderDualTriggerAlgebraUp$ and $\FieldFaithful\ \AlexanderDualTriggerAlgebraUp$ instances preserving $B,T,I,U,L,R,H,C,P,N$ as separate displayed fields.

\closureat{AlexanderDualTriggerAlgebraUp}{seedStr}

\begin{closurestatus}{\AlexanderDualTriggerAlgebraUp}
  \constructivestory{An $\AlexanderDualTriggerAlgebraUp$ packet is generated from boundary-tile rows, trigger rows, inactive-face rows, blocker-dual cover rows, finite Bool and observation ledgers, algebra transport, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:alexander-dual-trigger-algebra-carrier}, \autoref{thm:alexander-dual-trigger-algebra-namecert-obligations}, and \autoref{thm:alexander-dual-trigger-algebra-blocker-duality-nonescape} seed the finite Alexander-dual trigger and blocker NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host polynomial equality, ambient monomial ideals, stochastic biological dynamics, quotient codon equality, infinite trigger search, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, trigger-row exposure, blocker-dual cover exactness, inactive-face accounting, finite tag and observation ledgers, algebra transport, Nontrivial AlexanderDualTriggerAlgebraUp, and FieldFaithful AlexanderDualTriggerAlgebraUp for BEDC.Derived.AlexanderDualTriggerAlgebraUp.}
\end{closurestatus}
