\chapter{A Concrete Naming Certificate for $\BaireTwoFunctionUp$}
\label{ch:concrete-instances-baire-two-function-namecert}
\origin{human}

Following Baire and classical descriptive set theory, the $\BaireTwoFunctionUp$ packet records the successor step from Baire-one real-valued maps to pointwise limits of Baire-one approximants as finite BEDC NameCert data. It sits over the $\BaireOneFunctionUp$ surface of \autoref{ch:concrete-instances-baireonefunction-namecert}, the finite schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-value seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only the displayed approximation ladder and its finite read route; it is not a host function-space quotient, a selected limiting function, a measurability theorem, or an ambient completeness assertion.

\begin{definition}[BaireTwoFunction carrier]
\label{def:baire-two-function-carrier}
A $\BaireTwoFunctionUp$ carrier is a finite $\BHist$ packet
$$
T=(B,A,S,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the source $\BaireOneFunctionUp$ approximation-ladder row, listing the Baire-one packets whose pointwise observations are being inspected.
\item $A$ is the finite ladder-admission row, naming the displayed source points, approximation indices, and precision requests visible to the successor packet.
\item $S$ is the $\StreamNameUp$ schedule row selecting the finite approximation windows opened for each displayed request.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational windows obtained from the selected Baire-one observations.
\item $R$ is the terminal $\RealUp$ seal reached only after the Baire-one ladder, displayed schedule, and regular rational readback have been replayed.
\item $H$ records componentwise $\hsame$ transport for the Baire-one ladder, finite admission row, schedule windows, rational readback, real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a pointwise successor request through the Baire-one ladder, the stream schedule, the rational readback, the real seal, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\BaireTwoFunctionUp$, $\BaireOneFunctionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BaireTwoFunctionUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host space of Baire-two functions, an arbitrary selected approximating ladder, quotient equality of real names, full Borel hierarchy closure, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[BaireTwoFunction NameCert obligations]
\label{thm:baire-two-function-namecert-obligations}
For every accepted $\BaireTwoFunctionUp$ carrier $T=(B,A,S,Q,R,H,C,P,N)$, the local $\NameCert_{\BaireTwoFunctionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the Baire-one approximation ladder, ladder-admission row, schedule windows, rational readback, real seal, componentwise transport, displayed continuation, provenance, and local naming rows;
\item Baire-one ladder exposure, requiring every successor observation to pass first through a displayed $\BaireOneFunctionUp$ row in $B$;
\item schedule exactness, requiring every approximation request to use only the finite $\StreamNameUp$ windows named by $S$ after the ladder-admission row $A$ is displayed;
\item readback exactness, requiring the value read to pass through the $\RegSeqRatUp$ row $Q$ before the $\RealUp$ seal $R$ is available;
\item transport and replay stability, requiring $H$ and $C$ to preserve the same route $B,A,S,Q,R$ componentwise;
\item ledger refusal, excluding host function-space quotients, selected limiting functions, arbitrary ladder choice, quotient equality of real names, full Borel hierarchy closure, and ambient $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:baire-two-function-carrier}. The rows $B,A,S,Q,R$ are the only analytic rows available to a consumer, and $H,C,P,N$ are the only structural rows attached to them.

The successor step begins with the Baire-one ladder $B$. The admission row $A$ fixes the displayed source points, approximation indices, and precision requests before any schedule window can be opened.

The schedule and readback rows then force the finite route. A request reads the $\StreamNameUp$ windows in $S$, checks the selected observations through the $\RegSeqRatUp$ row $Q$, and reaches the $\RealUp$ seal $R$ only after those rows have been replayed.

Transport, continuation, provenance, and local naming preserve exactly this route. Since no carrier coordinate stores a host function space, selected limiting function, arbitrary ladder choice, quotient real equality, full Borel hierarchy closure, or ambient real completeness, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[BaireTwoFunction Baire-one handoff]
\label{thm:baire-two-function-baire-one-handoff}
Every $\BaireOneFunctionUp$ approximation consumed by an accepted $\BaireTwoFunctionUp$ packet is read before the $\StreamNameUp$ schedule, $\RegSeqRatUp$ readback, and $\RealUp$ seal. Thus every successor value exported by the packet factors through
$$
B,A,S,Q \longmapsto R .
$$
The handoff exposes a finite pointwise successor route from Baire-one data to real seals and exports no host function-space quotient, selected limiting function, arbitrary ladder selector, quotient equality of real names, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Start with a consumer of the value seal $R$. By carrier admission, $R$ is downstream of the same packet that contains the Baire-one ladder $B$, the admission row $A$, the schedule $S$, and the readback row $Q$.

Replay the continuation row $C$. The consumer first reads a displayed $\BaireOneFunctionUp$ approximation from $B$, then uses $A$ to identify the pointwise request and the finite approximation window available to the packet.

The schedule row $S$ selects only those displayed windows, and the regular rational row $Q$ reads the selected observations before $R$ is exposed. Componentwise transport by $H$ preserves this order for every accepted carrier.

The provenance and local naming rows contain no host function-space quotient, selected limiting function, arbitrary ladder selector, quotient real equality, or ambient completeness coordinate. Hence the exported successor value is only the displayed finite Baire-one handoff.
\end{proof}

\closureat{BaireTwoFunctionUp}{seedStr}

\begin{closurestatus}{\BaireTwoFunctionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:baire-two-function-carrier}, \autoref{thm:baire-two-function-namecert-obligations}, and \autoref{thm:baire-two-function-baire-one-handoff} seed the finite Baire-two successor packet over Baire-one ladders, finite schedules, rational readback, real sealing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host function-space quotients, selected limiting functions, arbitrary ladder choice, quotient equality of real names, full Borel hierarchy closure, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Baire-one ladder exposure, schedule exactness, rational readback exactness, real-seal nonescape, transport stability, provenance, and ledger refusal for BEDC.Derived.BaireTwoFunctionUp.}
  \constructivestory{A $\BaireTwoFunctionUp$ packet is generated from a BaireOneFunction approximation ladder, finite request admission, StreamName schedule windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
