\chapter{A Concrete Naming Certificate for $\GDeltaSetUp$}
\label{ch:concrete-instances-g-delta-set-namecert}
\origin{human}

Following Kechris and Engelking on Polish spaces and descriptive set theory, the $\GDeltaSetUp$ packet records the traditional countable-intersection-of-open-sets interface as finite BEDC NameCert data. It sits over the complete separable metric source of \autoref{ch:concrete-instances-polishspace-namecert}, the generated-set boundary of \autoref{ch:concrete-instances-borel-set-namecert}, the countable-base discipline of \autoref{ch:concrete-instances-second-countable-namecert}, and the indexed density surface of \autoref{ch:concrete-instances-countable-dense-subset-namecert}. The packet names the route by which Polish and Borel consumers inspect a displayed open-row schedule without importing a host subset, selected enumeration, classical complement closure, ambient countable choice, or a standard descriptive-set theorem.

\begin{definition}[GDeltaSet carrier]
\label{def:g-delta-set-carrier}
A $\GDeltaSetUp$ carrier is a finite $\BHist$ packet
$$
G=(P,B,S,W,O,H,C,L,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the Polish and second-countable source row. It exposes the $\PolishSpaceUp$ complete-separable metric packet, the $\SecondCountableUp$ base row, and the $\CountableDenseSubsetUp$ indexed-density handoff visible to the current consumer.
\item $B$ is the $\BorelSetUp$ row that receives the generated-set handoff after the displayed open schedule has been inspected.
\item $S$ is the countable open-row schedule. Each finite prefix names the open rows whose intersection is being offered, together with the schedule position and the source row over which the open row is read.
\item $W$ is the finite $\StreamNameUp$ window row. It records exactly the schedule positions, base-cell indices, density indices, and finite query windows visible before the consumer reads the Borel row.
\item $O$ is the open-set readback row, carrying the displayed open classifier, local basis witness, and source compatibility proof for every open row inspected through $S$ and $W$.
\item $H$ records componentwise $\hsame$ transport for the Polish source, Borel row, open schedule, stream windows, open readback, continuation replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Polish or Borel query through $P,S,W,O$ before the generated-set row $B$ is consumed.
\item $L$ is the $\Pkg$ provenance over $\GDeltaSetUp$, $\PolishSpaceUp$, $\BorelSetUp$, $\SecondCountableUp$, $\CountableDenseSubsetUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\GDeltaSetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $P,B,S,W,O,H,C,L,N$. It has no coordinate for host subsets, chosen countable enumerations, ambient countable choice, quotient set equality, classical complement closure, or standard descriptive-set transfer theorems.
\end{definition}

\begin{theorem}[GDeltaSet NameCert obligations]
\label{thm:g-delta-set-namecert-obligations}
For every accepted $\GDeltaSetUp$ carrier $G=(P,B,S,W,O,H,C,L,N)$, the local $\NameCert_{\GDeltaSetUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the Polish and second-countable source row, Borel row, open-row schedule, finite windows, open readback, transport, replay, provenance, and local naming;
\item countable schedule exposure, requiring every inspected intersection stage to appear as a displayed finite prefix of $S$ before it reaches $B$;
\item finite-window stability, requiring each schedule position, base-cell index, density index, and query window to be read through $W$;
\item open-row readback, requiring each open component to pass through the classifier and local-basis data stored in $O$ over the same source row $P$;
\item Borel and Polish handoff, requiring the generated-set row $B$ to consume only the displayed route through $P,S,W,O$;
\item componentwise transport, requiring $H$ to preserve the source, schedule, windows, open readback, Borel row, replay, provenance, and local name together;
\item continuation replay, requiring $C$ to replay the same ordered route before any Polish or Borel consumer receives the packet;
\item provenance, requiring $L$ to name exactly the displayed sibling packets and BEDC kernel rows used by the carrier;
\item local naming, requiring $N$ to certify only the rows $P,B,S,W,O,H,C,L$;
\item ledger refusal, excluding host countable choice, quotient set equality, selected enumerations, host subsets, classical complement closure, and ambient descriptive-set theorems.
\end{enumerate}
No $\GDeltaSetUp$ NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:g-delta-set-carrier}. The tuple displays exactly the Polish and second-countable source row, Borel row, countable open-row schedule, finite stream windows, open readback row, transport, replay, provenance, and local naming.

The schedule exposure and finite-window obligations are read through $S$ and $W$. A consumer sees only a finite prefix of the countable open schedule, and each schedule position, base-cell index, density index, and query window is inspected through the same displayed stream-window row.

Open-row readback is forced by $O$ over the source row $P$. Thus each open component is tied to the Polish, second-countable, and indexed-density data before the generated-set row $B$ can be consumed.

Finally $H,C,L,N$ transport, replay, source, and name the same route. Since no listed row stores a host subset, chosen enumeration, countable-choice selector, quotient set equality, classical complement closure, or standard descriptive-set theorem, the enumerated obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[GDeltaSet Polish-Borel handoff]
\label{thm:g-delta-set-polish-borel-handoff}
Every Polish or Borel consumer of an accepted $\GDeltaSetUp$ packet factors through the displayed route
$$
\PolishSpaceUp,\ \SecondCountableUp,\ \CountableDenseSubsetUp,\ \StreamNameUp
\longmapsto
\BorelSetUp .
$$
More precisely, the consumer first reads the source row $P$, then the schedule and finite windows $S,W$, then the open-row readback $O$, and only then the generated-set row $B$. The exported object is a finite NameCert packet for the displayed countable open-row route; it is not a host subset, a chosen enumeration, a classical complement-closure proof, an ambient standard descriptive-set theorem, or a quotient set equality.
\end{theorem}
\begin{proof}
Begin with a Polish or Borel consumer of the accepted packet. Carrier admission provides the source row $P$, but no generated-set read is available until the open schedule and window rows have been displayed.

Replay the continuation row $C$. The read moves through $S$ and $W$, so every countable-intersection stage is consumed only as a finite visible prefix with finite schedule, base-cell, density, and query observations.

The open readback row $O$ then ties the visible open components back to the Polish and second-countable source. After that readback, the Borel row $B$ receives the generated-set handoff.

The remaining rows $H,L,N$ preserve, source, and name the same route. Therefore every consumer factors through the displayed schedule, window, and open-row route, with no host subset, chosen enumeration, classical complement closure, standard descriptive-set theorem, or quotient set equality exported by the packet.
\end{proof}

\closureat{GDeltaSetUp}{seedStr}

\begin{closurestatus}{\GDeltaSetUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:g-delta-set-carrier}, \autoref{thm:g-delta-set-namecert-obligations}, and \autoref{thm:g-delta-set-polish-borel-handoff} seed the finite GDeltaSet route over Polish, second-countable, countable-dense, StreamName, open-readback, Borel, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host subsets, selected countable enumerations, countable choice, quotient set equality, classical complement closure, standard descriptive-set theorems, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, countable schedule exposure, finite-window stability, open-row readback, Polish-Borel handoff, transport, replay, provenance, local naming, and ledger refusal for BEDC.Derived.GDeltaSetUp.}
  \constructivestory{A $\GDeltaSetUp$ packet is generated from a Polish and second-countable source row, a BorelSet row, a countable open-row schedule, finite StreamName windows, open-set readback rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
