\chapter{A Concrete Naming Certificate for $\CompleteMetricBaireSurfaceUp$}
\label{ch:concrete-instances-complete-metric-baire-surface-namecert}
\origin{human}

Following Baire and Oxtoby, the $\CompleteMetricBaireSurfaceUp$ packet records the textbook complete-metric Baire argument as finite BEDC NameCert rows rather than as an ambient host theorem. It sits over the dense-open schedule of \autoref{ch:concrete-instances-bairecategory-namecert}, the Cauchy-thread and limit-service row of \autoref{ch:concrete-instances-completemetric-namecert}, the metric carrier rows of \autoref{ch:concrete-instances-metric-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the surface on which a Baire dense-open construction can be inspected before any countable-choice selector, host intersection, open-cover compactness theorem, or ambient $\RealUp$ completeness claim is available.

\begin{definition}[CompleteMetricBaireSurface carrier]
\label{def:complete-metric-baire-surface-carrier}
A $\CompleteMetricBaireSurfaceUp$ carrier is a finite $\BHist$ packet
$$
U=(B,K,M,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BaireCategoryUp$ dense-open schedule row, listing the finite dense-open requests and the predecessor-ball refinements made visible to the packet.
\item $K$ is the $\CompleteMetricUp$ Cauchy-thread row, exposing only the displayed center sequence, radius shrinkage, and limit-service handoff used by the dense-open route.
\item $M$ is the $\MetricSpaceUp$ carrier row, naming the distance, ball classifier, and metric comparison data consumed by $B$ and $K$.
\item $S$ is the $\StreamNameUp$ finite-window row through which the schedule, centers, radii, and requested tolerances are inspected.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational center and radius data visible before the terminal seal.
\item $E$ is the $\RealUp$ seal reached only after the schedule, Cauchy thread, metric carrier, finite windows, and rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the dense-open schedule, complete-metric thread, metric carrier, finite windows, rational readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the same dense-open, Cauchy-thread, metric, window, readback, and seal route.
\item $P$ is the $\Pkg$ provenance over $\CompleteMetricBaireSurfaceUp$, $\BaireCategoryUp$, $\CompleteMetricUp$, $\MetricSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompleteMetricBaireSurfaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for countable choice, host intersections, open-cover compactness, selected limit points, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.CompleteMetricBaireSurfaceUp.CompleteMetricBaireSurfaceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Baire-category complete-metric NameCert surface]
\label{thm:baire-category-complete-metric-namecert-surface}
For every accepted $\CompleteMetricBaireSurfaceUp$ carrier
$$
U=(B,K,M,S,R,E,H,C,P,N),
$$
the local $\NameCert_{\CompleteMetricBaireSurfaceUp}$ surface exposes exactly the Baire dense-open schedule, complete-metric Cauchy thread, metric carrier rows, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming row. Every complete-metric Baire read is routed through $B,K,M,S,R,E,H,C,P,N$, and no obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:complete-metric-baire-surface-carrier}. The rows $B,K,M,S,R,E$ are the only analytic rows available to a consumer: dense-open schedule, Cauchy-thread service, metric carrier, finite windows, rational readback, and terminal real seal.

The Baire-category content is read first through $B$. Each dense-open request and predecessor-ball refinement is displayed as finite schedule data, then the complete-metric row $K$ carries the Cauchy thread built from those refinements.

The numerical and metric observations are constrained by $M,S,R,E$. The metric carrier supplies distance and ball comparisons, the stream row supplies finite inspection windows, the regular rational row reads center and radius data, and the real seal is reached only after those rows have been displayed.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier contains no coordinate for countable choice, host intersections, open-cover compactness, selected limit points, ambient real completeness, Lean verification, or bridge checking, the listed rows exhaust the local NameCert surface.
\end{proof}

\closureat{CompleteMetricBaireSurfaceUp}{seedStr}

\begin{closurestatus}{\CompleteMetricBaireSurfaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-metric-baire-surface-carrier} and \autoref{thm:baire-category-complete-metric-namecert-surface} seed the complete-metric Baire surface over dense-open schedules, Cauchy-thread rows, metric carriers, finite windows, rational readback, real sealing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, host intersections, open-cover compactness, selected limit points, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-open schedule exposure, complete-metric Cauchy-thread exactness, finite-window readback, rational center readback, real sealing, and nonescape for BEDC.Derived.CompleteMetricBaireSurfaceUp.}
  \constructivestory{A $\CompleteMetricBaireSurfaceUp$ packet is generated from a BaireCategory dense-open schedule, a CompleteMetric Cauchy thread, MetricSpace carrier rows, StreamName finite windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
