\chapter{A Concrete Naming Certificate for $\CompactSourceTriangleEstimateUp$}
\label{ch:concrete-instances-compact-source-triangle-estimate-namecert}
\origin{human}

Following the finite-net proof of compact uniform continuity in \autoref{ch:visions-compact-uniform-continuity}, the $\CompactSourceTriangleEstimateUp$ packet records the residual triangle-estimate surface that remains after a compact source, continuous-map pointwise modulus, and uniform-modulus candidate have already been displayed. It sits over the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map carrier of \autoref{ch:concrete-instances-continuousmap-namecert}, the metric triangle estimate packet of \autoref{ch:concrete-instances-metric-triangle-uniform-estimate-namecert}, and the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet names the final source-and-target triangle ledger only; it is not a compactness theorem, not a pointwise-modulus selector, not a finite-net constructor, and not a host proof of Heine--Cantor.

\begin{definition}[Compact-source triangle estimate carrier]
\label{def:compact-source-triangle-estimate-carrier}
A $\CompactSourceTriangleEstimateUp$ carrier is a finite $\BHist$ packet
$$
T=(K,F,U,E,S,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row, exposing the finite-net coverage and located-distance comparisons for the compact source metric.
\item $F$ is the $\ContinuousMapUp$ row whose pointwise modulus and graph evaluations are inspected on the same compact source.
\item $U$ is the $\UniformModulusUp$ candidate row produced by the finite-net lower-bound route.
\item $E$ is the $\MetricTriangleUniformEstimateUp$ residual row, recording the source triangle estimate around a selected net center and the target triangle estimate for the two image points.
\item $S$ is the finite center-radius ledger that ties the selected compact-source probe to the pointwise modulus radius and to the uniform-modulus precision.
\item $R$ is the $\RatUp$ comparison ledger for the epsilon-third, half-radius, and lower-bound inequalities used by $E$.
\item $L$ is the local nonescape ledger saying that the estimate consumes only the displayed compact source, continuous-map graph, uniform-modulus candidate, triangle-estimate row, and rational comparisons.
\item $H$ records componentwise $\hsame$ transport for the compact source, continuous map, uniform-modulus candidate, triangle estimate, center-radius ledger, rational comparison ledger, nonescape ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact-uniform-continuity request through $K,F,U,E,S,R,L$.
\item $P$ is the $\Pkg$ provenance over $\CompactSourceTriangleEstimateUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\MetricTriangleUniformEstimateUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactSourceTriangleEstimateUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an open cover, an external finite subset, a selected point outside the displayed probe row, a host supremum norm, or an independent Heine--Cantor theorem.
\end{definition}

\begin{theorem}[Compact-source triangle estimate NameCert obligations]
\label{thm:compact-source-triangle-estimate-namecert-obligations}
For every accepted $\CompactSourceTriangleEstimateUp$ carrier
$$
T=(K,F,U,E,S,R,L,H,C,P,N),
$$
the local $\NameCert_{\CompactSourceTriangleEstimateUp}$ surface consists exactly of carrier admission for the compact metric source, continuous-map row, uniform-modulus candidate, metric triangle estimate, finite center-radius ledger, rational comparison ledger, local nonescape ledger, componentwise transport, displayed continuation replay, package provenance, and local naming; compact-source compatibility between $K$ and the source row of $F$; triangle-estimate exactness through $E$; rational-bound exactness through $R$; and refusal of open covers, external finite subsets, hidden point selectors, host norms, and independent Heine--Cantor reasoning.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-source-triangle-estimate-carrier}. The accepted packet displays the compact source, continuous map, uniform-modulus candidate, triangle estimate, center-radius ledger, rational comparisons, and structural rows.

Compact-source compatibility is read first. The compact row $K$ and continuous-map row $F$ name the same source metric before any center-radius estimate in $S$ can be consumed.

The residual estimate is the row $E$. It combines the source triangle comparison around the displayed compact-net center with the target triangle comparison for the two image points, while $R$ records the epsilon-third and radius inequalities used by that comparison.

The rows $L,H,C,P,N$ record nonescape, transport, replay, provenance, and naming. Since no excluded coordinate appears in the carrier, the packet cannot export an open cover, external finite subset, hidden selector, host norm, or independent Heine--Cantor proof.
\end{proof}

\begin{theorem}[Compact-source triangle estimate UniformModulus handoff]
\label{thm:compact-source-triangle-estimate-uniformmodulus-handoff}
Every $\UniformModulusUp$ consumer of an accepted $\CompactSourceTriangleEstimateUp$ packet must read the compact source, continuous-map graph, uniform-modulus candidate, metric triangle estimate, finite center-radius ledger, rational comparison ledger, and nonescape ledger before it reads the structural rows
$$
H,C,P,N .
$$
Consequently the consumer receives a final compact-source triangle residual over $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, and $\MetricTriangleUniformEstimateUp$, rather than a new compactness or continuity principle.
\end{theorem}
\begin{proof}
Start with the accepted carrier $T=(K,F,U,E,S,R,L,H,C,P,N)$. The uniform-modulus consumer can read $U$ only after $K$ and $F$ have identified the compact source and graph surface.

The estimate then passes through $S,R,E$. The center-radius ledger ties the selected compact-source probe to the pointwise-modulus radius and uniform precision, the rational ledger records the required inequalities, and the metric triangle estimate row supplies the source and target triangle steps.

The nonescape ledger $L$ and structural rows $H,C,P,N$ preserve the same route. Thus the handoff is a residual triangle-estimate packet for an already displayed compact-uniform route, not an additional source of compactness or continuity data.
\end{proof}

\falsifiablePrediction{Every accepted $\CompactSourceTriangleEstimateUp$ read must expose a $\CompactMetricUp$ source row, a $\ContinuousMapUp$ graph row over the same source, a $\UniformModulusUp$ candidate row, a $\MetricTriangleUniformEstimateUp$ residual row, finite center-radius and rational comparison ledgers, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{compactmetric, continuousmap, uniformmodulus, metric-triangle-uniform-estimate: $\CompactSourceTriangleEstimateUp$ is not bijective to any listed sibling because it binds the final compact-source triangle residual after the finite-net and pointwise-modulus data have already been displayed.}

\closureat{CompactSourceTriangleEstimateUp}{seedStr}

\begin{closurestatus}{\CompactSourceTriangleEstimateUp}
  \constructivestory{A $\CompactSourceTriangleEstimateUp$ packet is generated from a CompactMetric source row, ContinuousMap graph row, UniformModulus candidate row, MetricTriangleUniformEstimate residual row, finite center-radius ledger, RatUp comparison ledger, local nonescape ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-source-triangle-estimate-carrier}, \autoref{thm:compact-source-triangle-estimate-namecert-obligations}, and \autoref{thm:compact-source-triangle-estimate-uniformmodulus-handoff} seed the final compact-source triangle residual consumed by the compact-uniform-continuity route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close compactness, pointwise continuity, finite-net construction, selected centers outside displayed probes, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-source compatibility, triangle-estimate exactness, rational-bound exactness, UniformModulus handoff, nonescape, and TasteGate field faithfulness for BEDC.Derived.CompactSourceTriangleEstimateUp.}
\end{closurestatus}
