\chapter{A Concrete Naming Certificate for $\CompactTotallyBoundedUp$}
\label{ch:concrete-instances-compact-totally-bounded-namecert}
\origin{human}

Following Bishop and Bridges, the $\CompactTotallyBoundedUp$ packet records the constructive compact-metric surface obtained from a complete metric carrier with explicit finite nets at visible positive radii. It sits between the finite-net interface of \autoref{ch:concrete-instances-totallybounded-namecert}, the limit-service interface of \autoref{ch:concrete-instances-completemetric-namecert}, and the compact-metric interface of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet names the finite bridge used by compact and continuous arguments; it does not turn metric compactness into open-cover compactness, selected limits, quotient equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Compact totally bounded carrier]
\label{def:compact-totally-bounded-carrier}
A $\CompactTotallyBoundedUp$ carrier is a finite $\BHist$ packet
$$
J=(M,C,T,N,E,H,K,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ metric row, including the point carrier, point classifier, distance witness relation, and rational comparison ledger used by every compactness read.
\item $C$ is the $\CompleteMetricUp$ limit-service row. It records only displayed regular Cauchy streams, moduli, limit histories, and late-distance ledgers available inside the metric carrier.
\item $T$ is the $\TotallyBoundedUp$ finite-net row. For each visible positive radius it exposes a closed $\ProbeBundle$ of center histories, membership constructors, and coverage witnesses.
\item $N$ is the net-radius schedule. It records the positive $\RatUp$ radii at which the finite-net rows are read and the refinement relation between requested tolerances and displayed net radii.
\item $E$ is the exactness row tying $M,C,T,N$ together. It says that each distance comparison used by $T$ and each convergence comparison used by $C$ is a row of the same metric source $M$.
\item $H$ records componentwise $\hsame$ transport for the metric, complete-metric, totally-bounded, radius, exactness, replay, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay from a compactness request through $M,C,T,N,E,H,P,L$.
\item $P$ is the $\Pkg$ provenance over $\CompactTotallyBoundedUp$, $\MetricSpaceUp$, $\CompleteMetricUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\RatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\CompactTotallyBoundedUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $M,C,T,N,E,H,K,P,L$. It has no coordinate for open covers, selected subcovers, quotient metric points, host equality of Cauchy streams, a choice-selected finite net, or ambient real completeness.
\end{definition}

\begin{theorem}[Compact totally bounded carrier admission]
\label{thm:compact-totally-bounded-carrier-admission}
For every accepted $\CompactTotallyBoundedUp$ carrier $J=(M,C,T,N,E,H,K,P,L)$, the local carrier admits exactly the metric source, complete-metric limit service, totally-bounded finite-net family, radius schedule, exactness row, transport row, replay row, provenance row, and local naming row displayed in \autoref{def:compact-totally-bounded-carrier}.
\end{theorem}
\begin{proof}
Project the accepted packet. The mathematical rows are $M,C,T,N,E$, and the structural rows are $H,K,P,L$.

No other coordinate is present in the carrier. Hence any accepted packet is admitted through exactly those rows, with the metric, completion, finite-net, radius, exactness, transport, replay, provenance, and naming data listed in the definition.
\end{proof}

\begin{theorem}[Compact totally bounded classifier stability]
\label{thm:compact-totally-bounded-classifier-stability}
The classifier of an accepted $\CompactTotallyBoundedUp$ carrier is stable under componentwise $\hsame$ transport of the metric row, complete-metric row, totally-bounded finite-net row, radius schedule, and exactness row. The transported packet has the same displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ surface.
\end{theorem}
\begin{proof}
Use the row $H$. It records componentwise transport for $M,C,T,N,E$ and for the structural rows.

The replay row $K$ reads only the transported coordinates, and $P,L$ record only the same provenance and local naming after transport. Thus the classifier cannot change by moving to an unrecorded metric, net family, limit service, or host compactness principle.
\end{proof}

\begin{theorem}[Compact totally bounded finite-net exhaustion]
\label{thm:compact-totally-bounded-finite-net-exhaustion}
Every compactness read from an accepted $\CompactTotallyBoundedUp$ carrier factors its finite coverage demand through the displayed $\TotallyBoundedUp$ row $T$ and the radius schedule $N$. For each requested positive tolerance, the read obtains only the closed $\ProbeBundle$ centers, membership rows, metric coverage rows, and rational comparison ledgers exposed by those two rows.
\end{theorem}
\begin{proof}
Begin with a compactness read and inspect the finite-net coordinate. The only available finite-net family is $T$.

The radius at which the finite net is consumed is not chosen externally. It is read from $N$, and the exactness row $E$ ties the resulting coverage distances back to the metric row $M$.

Therefore finite coverage is exhausted by $T,N,E$ over the metric source. A host enumeration, a selected finite subcover, or an ambient compactness theorem has no row in the packet.
\end{proof}

\begin{theorem}[Compact totally bounded completion handoff]
\label{thm:compact-totally-bounded-completion-handoff}
Every Cauchy or completion-facing read from an accepted $\CompactTotallyBoundedUp$ carrier reaches the complete-metric service only through the displayed row $C$, after the same metric row $M$ and exactness row $E$ have been fixed. The handoff exports no selected limit outside the carrier and no quotient equality of Cauchy names.
\end{theorem}
\begin{proof}
The complete-metric coordinate is $C$. It names the displayed streams, moduli, limit histories, and late-distance ledgers available in the carrier.

The row $E$ ties those convergence comparisons to $M$, so a completion-facing consumer cannot replace the metric source or import a host equality of Cauchy names.

Since the carrier contains no selector outside $C$ and no quotient coordinate, the completion handoff remains the displayed finite BEDC route.
\end{proof}

\begin{theorem}[Compact totally bounded nonescape]
\label{thm:compact-totally-bounded-nonescape}
No accepted $\CompactTotallyBoundedUp$ packet exports open-cover compactness, selected subcovers, selected limits, quotient equality, countable choice, or ambient $\RealUp$ completeness. Its compact-metric content is exactly the finite route
$$
M,C,T,N,E,H,K,P,L .
$$
\end{theorem}
\begin{proof}
Apply the carrier admission theorem. Every public read of the packet factors through the displayed tuple $M,C,T,N,E,H,K,P,L$.

Finite coverage is confined to $T,N,E$, and completion service is confined to $C,E$. The transport, replay, provenance, and local naming rows preserve those routes.

The excluded principles do not occur among the carrier coordinates. They therefore cannot be exported by an accepted packet without leaving the local $\CompactTotallyBoundedUp$ NameCert surface.
\end{proof}

\closureat{CompactTotallyBoundedUp}{seedStr}

\begin{closurestatus}{\CompactTotallyBoundedUp}
  \constructivestory{A $\CompactTotallyBoundedUp$ packet is generated from a MetricSpace row, CompleteMetric limit-service row, TotallyBounded finite-net row, net-radius schedule, exactness row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-totally-bounded-carrier}, \autoref{thm:compact-totally-bounded-carrier-admission}, \autoref{thm:compact-totally-bounded-classifier-stability}, \autoref{thm:compact-totally-bounded-finite-net-exhaustion}, \autoref{thm:compact-totally-bounded-completion-handoff}, and \autoref{thm:compact-totally-bounded-nonescape} seed the constructive compact-metric bridge from complete metric service and finite total-bounded nets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected subcovers, selected limits, quotient equality, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, finite-net exhaustion, completion handoff, nonescape, and local NameCert registration for BEDC.Derived.CompactTotallyBoundedUp.}
\end{closurestatus}
