\chapter{A Concrete Naming Certificate for $\ConvexConjugateUp$}
\label{ch:concrete-instances-convex-conjugate-namecert}
\origin{human}

Following Rockafellar and Boyd--Vandenberghe, the $\ConvexConjugateUp$ packet names the Fenchel--Legendre conjugate surface by finite primal rows, dual rows, pairing evaluations, epigraph rows, and displayed supremum budgets. It sits over the convex-set, vector-space, real-name, and real-order interfaces of \autoref{ch:concrete-instances-convexset-namecert}, \autoref{ch:concrete-instances-vecspace-namecert}, \autoref{ch:concrete-instances-real-namecert}, and \autoref{sec:realalgorder-concrete-interface}, and it supplies the conjugacy handoff consumed by \autoref{ch:concrete-instances-fenchelduality-namecert}. The packet records conjugate data as BEDC carrier rows; it does not import host convex analysis, selected suprema, quotient function spaces, choice selectors, or ambient completeness.

\begin{definition}[Convex conjugate carrier]\label{def:convex-conjugate-carrier}
A $\ConvexConjugateUp$ carrier is a finite $\BHist$ packet
$$
K=(F,V,P,D,E,S,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the primal convex functional row, read through a displayed $\ConvexSetUp$ epigraph boundary.
\item $V$ is the dual-vector row over the visible $\VecSpaceUp$ dependency surface.
\item $P$ is the pairing-evaluation row that records the finite bilinear read used by the conjugate comparison.
\item $D$ is the domain and epigraph admission row tying the primal functional to the visible convex-set carrier.
\item $E$ is the extended-value comparison row, read through $\RealUp$ and the real-order interface.
\item $S$ is the supremum-budget row listing the finite inspected witnesses and the budget that prevents escape to a host supremum.
\item $H$ stores componentwise $\hsame$ transport for the primal row, dual vector, pairing row, epigraph row, comparison row, supremum budget, replay, provenance, and local naming.
\item $C$ stores displayed $\Cont$ replay from primal and dual reads to pairing evaluations, from pairing evaluations to epigraph comparisons, and from those comparisons to the budgeted conjugate row.
\item $Q$ is the $\Pkg$ provenance over $\ConvexConjugateUp$, $\FenchelDualityUp$, $\ConvexSetUp$, $\VecSpaceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ConvexConjugateUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,V,P,D,E,S,H,C,Q,N$. It has no coordinate for a host supremum operator, quotient function space, choice-selected maximizer, ambient dual-space completion, or external conjugacy theorem.
\end{definition}

\begin{theorem}[Convex conjugate NameCert obligations]\label{thm:convex-conjugate-namecert-obligations}
For every accepted $\ConvexConjugateUp$ carrier $K=(F,V,P,D,E,S,H,C,Q,N)$, the local $\NameCert_{\ConvexConjugateUp}$ surface consists exactly of carrier admission for the ten displayed rows, classifier stability under componentwise $\hsame$ transport, epigraph transport through the visible $\ConvexSetUp$ dependency, supremum-budget nonescape through $S$, and ledger visibility through the replay and provenance rows $C,Q,N$. Every conjugate read must pass through the primal functional row, dual-vector row, pairing evaluation row, epigraph row, extended-value comparison row, and displayed budget before a Fenchel-facing consumer can inspect it.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:convex-conjugate-carrier}. Its visible coordinates are exactly $F,V,P,D,E,S,H,C,Q,N$, so carrier admission and classifier comparison are componentwise on those rows.

The epigraph and comparison clauses route every primal functional read through $\ConvexSetUp$, $\RealUp$, and the real-order interface before it can be paired with the dual row. Transport by $H$ and replay by $C$ preserve that displayed route.

The row $S$ is the only supremum-facing coordinate. Since the carrier has no host supremum, quotient function space, or selected maximizer field, the budgeted ledger $S,C,Q,N$ is the entire local NameCert surface available to downstream consumers.
\end{proof}

\begin{theorem}[Convex conjugate Fenchel handoff]\label{thm:convex-conjugate-fenchel-handoff}
Every $\FenchelDualityUp$ consumer that reads conjugacy through an accepted $\ConvexConjugateUp$ carrier receives only the displayed packet route
$$
F,V,P,D,E,S\longmapsto H,C,Q,N.
$$
The consumer reads primal functionals, dual vectors, pairings, epigraphs, extended-value comparisons, and supremum budgets through the $\ConvexConjugateUp$ packet, and receives no host supremum, quotient function space, choice selector, ambient completeness theorem, or external Fenchel conjugacy principle.
\end{theorem}
\begin{proof}
Use \autoref{thm:convex-conjugate-namecert-obligations}. It places every conjugate-facing read on the carrier rows $F,V,P,D,E,S$ before the structural rows $H,C,Q,N$ can replay or source the answer.

Now pass to the Fenchel-facing consumer. The consumer may cite the $\FenchelDualityUp$ packet only after the displayed conjugate rows have been read, so conjugacy enters as a finite BEDC row rather than as an analytic operation in the host language.

The excluded host objects are absent from \autoref{def:convex-conjugate-carrier}. Therefore the handoff supplies exactly the packet route and no selected supremum, quotient-function value, choice witness, completeness theorem, or external duality theorem.
\end{proof}

\falsifiablePrediction{Every $\ConvexConjugateUp$ consumer reads conjugacy through a primal functional row, dual-vector row, pairing-evaluation row, epigraph row, extended-value comparison row, supremum-budget row, transport, continuation replay, provenance, and local naming.}

\independenceWitness{convexset, vecspace, real, realalgorder, fenchelduality: $\ConvexConjugateUp$ is not bijective to any listed sibling because it jointly carries primal functional data, dual-vector data, pairing evaluation, epigraph comparison, a displayed supremum budget, transport, replay, provenance, and local naming.}

\closureat{ConvexConjugateUp}{seedStr}

\begin{closurestatus}{\ConvexConjugateUp}
  \constructivestory{A $\ConvexConjugateUp$ packet is generated from a primal convex functional row, a dual-vector row, a pairing-evaluation row, epigraph and extended-value comparison rows, a displayed supremum budget, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:convex-conjugate-carrier}, \autoref{thm:convex-conjugate-namecert-obligations}, and \autoref{thm:convex-conjugate-fenchel-handoff} bind the finite Fenchel--Legendre conjugate certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host convex analysis, selected suprema, quotient function spaces, choice selectors, ambient completeness, bridge checking, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, NameCert obligations, supremum-budget nonescape, Fenchel handoff, and TasteGate field faithfulness for BEDC.Derived.ConvexConjugateUp.}
\end{closurestatus}
