\chapter{A Concrete Naming Certificate for $\LocatedCompactIntervalOscillationBoundUp$}
\label{ch:concrete-instances-located-compact-interval-oscillation-bound-namecert}
\origin{human}

Following Bishop and Bridges on constructive compact intervals and finite moduli, the $\LocatedCompactIntervalOscillationBoundUp$ packet records the finite route by which a continuous map on a located compact interval receives a displayed oscillation bound from interval nets and dyadic tolerance ledgers. It sits after the finite-net source of \autoref{ch:concrete-instances-located-closed-interval-finite-net-namecert}, the compact interval surface of \autoref{ch:concrete-instances-located-interval-compactness-namecert}, the continuous-map graph rows of \autoref{ch:concrete-instances-continuousmap-namecert}, and the tolerance-window route of \autoref{ch:concrete-instances-oscillation-modulus-namecert}. The packet names only the L10 finite boundedness handoff through displayed rows; it does not assert Heine--Borel compactness, choice-selected extrema, quotient-real equality, host supremum existence, or ambient $\RealUp$ completeness.

\begin{definition}[Located compact interval oscillation-bound carrier]
\label{def:located-compact-interval-oscillation-bound-carrier}
A $\LocatedCompactIntervalOscillationBoundUp$ carrier is a finite $\BHist$ packet
$$
B=(I,K,F,N,M,D,W,R,E,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the located compact interval source row, read through the located endpoint and interval-compactness interfaces before any bound request is accepted.
\item $K$ is the $\LocatedIntervalCompactnessUp$ row recording the compact-interval admission used by the packet.
\item $F$ is the $\ContinuousMapUp$ graph row for the map whose interval oscillation is bounded.
\item $N$ is the $\LocatedClosedIntervalFiniteNetUp$ finite-net row, listing the inspected interval net and mesh scale.
\item $M$ is the $\OscillationModulusUp$ row converting the displayed oscillation request into a finite tolerance-window schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger carrying requested radii, mesh slack, and comparison budgets for $N$ and $M$.
\item $W$ is the $\StreamNameUp$ finite-window row used to inspect interval endpoints, net points, graph reads, and oscillation witnesses.
\item $R$ is the $\RegSeqRatUp$ readback row exposing the rational observations consumed by the oscillation bound.
\item $E$ is the terminal $\RealUp$ seal for the displayed bound, readable only after $I,K,F,N,M,D,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval, compactness, map, finite-net, modulus, tolerance, window, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the located interval and map rows through the finite net and oscillation modulus into the Real-facing seal.
\item $P$ is the $\Pkg$ provenance over $\LocatedCompactIntervalOscillationBoundUp$, $\LocatedIntervalCompactnessUp$, $\LocatedClosedIntervalFiniteNetUp$, $\ContinuousMapUp$, $\OscillationModulusUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\LocatedCompactIntervalOscillationBoundUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,K,F,N,M,D,W,R,E,H,C,P,L$. It has no coordinate for open-cover compactness, Heine--Borel subcovers, choice-selected extrema, quotient stream equality, host supremum data, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located compact interval oscillation-bound NameCert obligations]
\label{thm:located-compact-interval-oscillation-bound-namecert-obligations}
For every accepted $\LocatedCompactIntervalOscillationBoundUp$ carrier $B=(I,K,F,N,M,D,W,R,E,H,C,P,L)$, the local $\NameCert_{\LocatedCompactIntervalOscillationBoundUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located compact interval source, compactness row, continuous-map row, finite-net row, oscillation-modulus row, dyadic tolerance ledger, finite stream windows, rational readback, terminal Real seal, transport, replay, provenance, and local naming;
\item source compatibility, requiring $K$ and $F$ to read the same located interval source $I$ before the finite net or modulus is consumed;
\item finite-net exactness, requiring $N$ to expose the mesh and inspected net through $D$ and $W$ without importing an open-cover compactness theorem;
\item oscillation-modulus exactness, requiring $M$ to consume the displayed continuous-map row $F$ together with the finite net $N$ and the same dyadic tolerance ledger $D$;
\item Real seal nonescape, requiring the bound seal $E$ to be downstream of $I,K,F,N,M,D,W,R$ and forbidding choice-selected extrema, quotient-real equality, host supremum data, Lean verification, and bridge checking.
\end{enumerate}
No located compact interval oscillation-bound obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source rows are $I,K,F$, so the interval, compactness admission, and map graph are fixed before any finite net or oscillation modulus can be read.

The finite-net row $N$ then supplies the inspected mesh through the dyadic ledger $D$ and stream windows $W$. Because the carrier has no open-cover row or subcover selector, the net is only the displayed finite row inherited from the located interval route.

The oscillation-modulus row $M$ consumes the same map, net, tolerance, and window data. The readback row $R$ exposes the rational observations used by that modulus route before the terminal seal $E$ is available.

The structural rows $H,C,P,L$ transport, replay, source, and name this route. Since no coordinate stores Heine--Borel compactness, selected extrema, quotient equality, host supremum data, Lean verification, or bridge evidence, those objects cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[Located compact interval oscillation-bound route]
\label{thm:located-compact-interval-oscillation-bound-route}
Every accepted $\LocatedCompactIntervalOscillationBoundUp$ packet routes a Real-facing oscillation-bound read through
$$
\LocatedIntervalCompactnessUp,\ \ContinuousMapUp \longrightarrow \LocatedClosedIntervalFiniteNetUp \longrightarrow \OscillationModulusUp \longrightarrow \DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp \longrightarrow \RealUp .
$$
The route exposes the located compact interval source, continuous-map graph row, finite-net row, oscillation-modulus row, dyadic tolerance ledger, finite observation windows, rational readback, and terminal Real seal before any bound is consumed. A consumer that omits one of those rows is outside the accepted carrier.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:located-compact-interval-oscillation-bound-carrier}. The first analytic coordinates bind the located interval source, compactness admission, and continuous-map graph.

The finite-net coordinate $N$ supplies the inspected interval mesh. The oscillation-modulus coordinate $M$ then converts the displayed continuity and net data into a finite tolerance-window schedule using $D$ and $W$.

The rational readback $R$ and terminal seal $E$ are downstream of that schedule. Transport and replay preserve the same components, and provenance and local naming add no analytic row.

Thus every accepted bound follows the displayed route. If any row in the route is absent, the packet has no coordinate from which a Real-facing oscillation-bound read can be projected.
\end{proof}

\falsifiablePrediction{Every accepted $\LocatedCompactIntervalOscillationBoundUp$ consumer read factors through one located compact interval source, one ContinuousMap graph row, one LocatedClosedIntervalFiniteNet row, one OscillationModulus row, one DyadicRatCore tolerance ledger, one StreamName window, one RegSeqRat readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, local NameCert, and the terminal RealUp seal.}

\independenceWitness{located-closed-interval-finite-net, located-interval-compactness, continuousmap, oscillation-modulus: no listed sibling is bijective with $\LocatedCompactIntervalOscillationBoundUp$ because the packet jointly carries the compact interval source, continuous-map graph, finite-net mesh, oscillation-modulus schedule, dyadic tolerance ledger, finite windows, rational readback, Real-facing bound seal, transport, replay, provenance, and local naming.}

\closureat{LocatedCompactIntervalOscillationBoundUp}{seedStr}

\begin{closurestatus}{\LocatedCompactIntervalOscillationBoundUp}
  \constructivestory{A $\LocatedCompactIntervalOscillationBoundUp$ packet is generated from a located compact interval source row, a ContinuousMap graph row, a LocatedClosedIntervalFiniteNet mesh row, an OscillationModulus tolerance-window row, DyadicRatCore budgets, StreamName windows, RegSeqRat readback, a terminal RealUp bound seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-compact-interval-oscillation-bound-carrier}, \autoref{thm:located-compact-interval-oscillation-bound-namecert-obligations}, and \autoref{thm:located-compact-interval-oscillation-bound-route} seed the finite L10 oscillation-bound packet over located compact interval, continuous-map, finite-net, modulus, dyadic, window, readback, seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Heine--Borel compactness, selected extrema, quotient-real equality, host supremum data, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source compatibility, finite-net exactness, oscillation-modulus exactness, Real seal nonescape, transport replay, provenance exhaustion, and TasteGate field faithfulness for BEDC.Derived.LocatedCompactIntervalOscillationBoundUp.}
\end{closurestatus}
