\chapter{A Concrete Naming Certificate for $\TotallyBoundedUp$}
\label{ch:concrete-instances-totallybounded-namecert}

The totally-bounded interface $\TotallyBoundedUp$ packages a metric carrier admitting, for every $\varepsilon > 0$, an explicit finite $\varepsilon$-net. It depends on $\NameCert_{\MetricSpaceUp}$ (\autoref{ch:concrete-instances-metric-namecert}) and is the prerequisite for $\NameCert_{\CompactMetricUp}$ (\autoref{ch:concrete-instances-compactmetric-namecert}).

\section{Carrier definition}
\label{sec:totallybounded-carrier}

\begin{definition}[Totally bounded ProbeBundle net carrier]
\label{def:totallybounded-probebundle-net-carrier}
Let $X$ be a metric BEDC carrier whose distance rows are encoded by
$\mathsf{MetricDistanceWitness}$. A totally bounded ProbeBundle net carrier
at tolerance history $\varepsilon$ is the history relation
$$
\mathsf{TotallyBoundedProbeBundleNet}(X,\varepsilon,\mathcal{P},net)
$$
whose accepted row consists only of $\mathsf{BHist}$ ledger data:
\begin{enumerate}
  \item a positive $\NameCert_{\RatUp}$ tolerance history $\varepsilon$;
  \item a closed $\mathsf{ProbeBundle}$ $\mathcal{P}$ of center names;
  \item for every probe row $\mathsf{InBundle}(p,\mathcal{P})$, a center
  history $c_p$ admitted by the metric carrier $X$;
  \item for every such bundled probe, a positive $\NameCert_{\RatUp}$ radius
  history $r_p$;
  \item for every source-point history $x$ admitted by $X$, a bundled probe
  row $\mathsf{InBundle}(p,\mathcal{P})$, a distance history $d_p$, and a
  row $\mathsf{MetricDistanceWitness}(x,c_p,d_p)$ whose $\RatUp$ comparison
  ledger certifies $d_p \leq \varepsilon$.
\end{enumerate}
The finite carrier is the closed $\mathsf{ProbeBundle}$ inductive together
with the displayed $\mathsf{InBundle}$ coverage rows. It is not an external
enumeration of centers, and no host-level list is exposed as certificate data.
\end{definition}

\begin{theorem}[Totally bounded ProbeBundle net coverage stability]
\label{thm:totallybounded-probebundle-net-coverage-stability}
Let $X$ be a metric BEDC carrier with $\mathsf{MetricDistanceWitness}$
classifier transport. Suppose
$$
\mathsf{TotallyBoundedProbeBundleNet}(X,\varepsilon,\mathcal{P},net)
$$
holds. If the tolerance history $\varepsilon$, the bundled center histories
$c_p$, the positive radius histories $r_p$, and all displayed distance
histories $d_p$ are transported by $\hsame$, and if the positive-tolerance,
positive-radius, and bound comparisons are transported by the $\RatUp$
classifier, then the same $\mathsf{ProbeBundle}$ $\mathcal{P}$ with the
transported ledgers is again a valid totally bounded net for the transported
tolerance history.
\end{theorem}
\begin{proof}
Proceed by induction on the closed $\mathsf{ProbeBundle}$ spine. In the
$\Bnil$ case there is no bundled probe row to transport, and any accepted
coverage row is absent by inversion on $\mathsf{InBundle}$.

For a cons bundle $\Bcons(p,\mathcal{P}_0)$, the head probe is handled by the
head constructor of $\mathsf{InBundle}$ and the tail probes are handled by the
induction hypothesis through the tail constructor. The center history and the
positive radius history attached to each case are moved along the supplied
$\hsame$ rows, while the $\RatUp$ classifier transports positivity of the
radius ledger.

Now fix a transported source-point history $x'$. The original coverage row for
an $\hsame$ representative $x$ supplies a bundled probe $p$, a center $c_p$,
and a distance row $\mathsf{MetricDistanceWitness}(x,c_p,d_p)$ with
$d_p \leq \varepsilon$. Metric $\hsame$ transport carries this row to
$\mathsf{MetricDistanceWitness}(x',c'_p,d'_p)$ for the transported center and
distance histories.

It remains to repack the bound. The $\RatUp$ classifier transports the
comparison $d_p \leq \varepsilon$ to the comparison
$d'_p \leq \varepsilon'$, and the same $\mathsf{InBundle}(p,\mathcal{P})$
constructor records that the chosen probe still belongs to the finite carrier.
Thus the transported ledgers satisfy the carrier relation for the same closed
bundle.
\end{proof}

\section{The certificate}
\label{sec:totallybounded-certificate}

\begin{theorem}[TotallyBoundedUp ProbeBundle NameCert target]
\label{thm:totallybounded-probebundle-net-namecert-target}
The carrier of \autoref{def:totallybounded-probebundle-net-carrier}, the
classifier given by transported tolerance and bundled ledger histories, the
coverage-stability theorem
\autoref{thm:totallybounded-probebundle-net-coverage-stability}, and the
ledger policy that records the tolerance, $\mathsf{ProbeBundle}$,
$\mathsf{InBundle}$ membership rows, center histories, positive radius
histories, $\mathsf{MetricDistanceWitness}$ rows, and $\RatUp$ bound rows form
the paper-level $\NameCert$ target for $\TotallyBoundedUp$ over a
$\MetricSpaceUp$ carrier.
\end{theorem}
\begin{proof}
The source field is the underlying $\MetricSpaceUp$ carrier together with its
accepted point histories and metric-distance classifier. The pattern field is
the relation
$\mathsf{TotallyBoundedProbeBundleNet}(X,\varepsilon,\mathcal{P},net)$ for
each positive $\RatUp$ tolerance history.

The classifier acts on the visible tolerance and on every bundled ledger row:
centers, radii, distance histories, and comparison proofs are transported by
the displayed $\hsame$ and $\RatUp$ classifier rows. The finite part of the
certificate is unchanged because $\mathcal{P}$ is the closed
$\mathsf{ProbeBundle}$ inductive and membership is witnessed by
$\mathsf{InBundle}$ constructors.

The stability obligation is exactly
\autoref{thm:totallybounded-probebundle-net-coverage-stability}. The ledger
policy records the same rows named in the carrier definition, so source
soundness, pattern soundness, classifier stability, and ledger soundness are
all witnessed by the displayed carrier and stability theorem. This is the
required current paper target for $\NameCert_{\TotallyBoundedUp}$.
\end{proof}
