\chapter{A Concrete Naming Certificate for $\MetaCICLocalDiamondWitnessUp$}
\label{ch:concrete-instances-metacic-local-diamond-witness-namecert}
\origin{ai}

The $\MetaCICLocalDiamondWitnessUp$ packet realizes the local-peak witness surface of \autoref{ch:metacic-confluence-audit-map} as finite BEDC confluence data. It sits beside the confluence audit packet of \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, the critical-path carrier of \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, the subject-reduction discharge socket of \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}, and the typed reduction trace of \autoref{ch:concrete-instances-typed-example-reduction-trace-namecert}. The packet names local peaks and candidate joins; it does not promote the conditional substitution boundary into a closed MetaCIC confluence theorem.

\falsifiablePrediction{Every accepted local-diamond witness has peak, left-step, right-step, candidate-join, closedness, transport, continuation, provenance, and naming rows.}

\independenceWitness{metacic-confluence-audit-packet, metacic-critical-path, subject-reduction-discharge-socket, metacic-subject-reduction-trace: the confluence audit packet records the global boundary without a per-peak witness carrier; the critical-path packet records priority and dependency pressure without candidate joins; the subject-reduction discharge socket records typing-side hypotheses without confluence joins; and the subject-reduction trace records reduction evidence without a local-diamond peak certificate. None is bijective to $\MetaCICLocalDiamondWitnessUp$.}

\begin{definition}[MetaCIC local-diamond witness carrier]
\label{def:metacic-local-diamond-witness-carrier}
A $\MetaCICLocalDiamondWitnessUp$ carrier is a finite $\BHist$ packet
$$
W=(K,L,R,J,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the peak row, naming the source term and the two outgoing MetaCIC reduction requests that form the local peak.
\item $L$ is the left-step row, recording the displayed one-step or parallel-step evidence for the left branch.
\item $R$ is the right-step row, recording the displayed one-step or parallel-step evidence for the right branch.
\item $J$ is the candidate-join row, listing the proposed common reduct together with the two displayed route requests into it.
\item $B$ is the closedness and boundary row, recording whether the witness is closed, normal-source, atom-source, or substitution-boundary conditional according to the confluence audit map.
\item $H$ records componentwise $\hsame$ transport for the peak, branch steps, candidate join, closedness boundary, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the peak through the two branch rows, then the candidate join, then the closedness boundary.
\item $P$ is the $\Pkg$ provenance over $\MetaCICLocalDiamondWitnessUp$, the MetaCIC confluence audit map, $\MetaCICConfluenceAuditPacketUp$, $\MetaCICCriticalPathUp$, $\SubjectReductionDischargeSocketUp$, $\TypedExampleReductionTraceUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetaCICLocalDiamondWitnessUp}$ row.
\end{enumerate}
The carrier exports no arbitrary closed Church--Rosser theorem, no proof of $\mathrm{BetaParallelSubstitutionCompatibility}$, no proof of $\mathrm{BetaParallelDiamondClosed}$, no subject-reduction theorem, and no host quotient equality of terms.
\end{definition}

\begin{theorem}[MetaCIC local-diamond witness NameCert obligations]
\label{thm:metacic-local-diamond-witness-namecert-obligations}
For every accepted $\MetaCICLocalDiamondWitnessUp$ carrier $W=(K,L,R,J,B,H,C,P,N)$, the local $\NameCert_{\MetaCICLocalDiamondWitnessUp}$ surface consists exactly of peak admission, left-step evidence, right-step evidence, candidate-join evidence, closedness and boundary classification, componentwise transport, displayed continuation replay, provenance, and local naming.

The Lean TasteGate follow-up must provide $\mathrm{Nontrivial}$ and $\mathrm{FieldFaithful}$ instances for the same carrier surface, so the witness cannot be collapsed to an empty marker and cannot hide a missing peak, branch, join, boundary, transport, replay, provenance, or naming coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-local-diamond-witness-carrier}. The peak row $K$ names the source and the two outgoing reduction requests, while $L$ and $R$ record the displayed branch evidence.

The join and boundary rows are then read in order. Row $J$ supplies the candidate common reduct and the route requests into it; row $B$ classifies the witness as closed, normal-source, atom-source, or substitution-boundary conditional.

The structural rows $H,C,P,N$ preserve and name that local peak route. Since the carrier contains no arbitrary closed Church--Rosser theorem, no substitution-compatibility proof, no closed parallel-diamond proof, no subject-reduction theorem, and no quotient equality of terms, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[MetaCIC local-diamond candidate-join exactness]
\label{thm:metacic-local-diamond-witness-candidate-join-exactness}
For every accepted $\MetaCICLocalDiamondWitnessUp$ carrier $W=(K,L,R,J,B,H,C,P,N)$, every candidate-join row $J$ is read only after the peak row $K$, left-step row $L$, right-step row $R$, and boundary row $B$ have been displayed through the same local-diamond witness packet. The row $J$ exports a candidate common reduct and the two route requests into it, but it exports no closed Church--Rosser theorem, no substitution-compatibility proof, no closed parallel-diamond proof, no subject-reduction theorem, and no quotient equality of terms.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-local-diamond-witness-carrier}. The NameCert obligations theorem \autoref{thm:metacic-local-diamond-witness-namecert-obligations} lists peak admission, left-step evidence, right-step evidence, candidate-join evidence, and closedness and boundary classification as the visible local-diamond rows.

Reading $J$ therefore occurs inside that listed route. The peak row $K$ fixes the source and outgoing requests; the branch rows $L$ and $R$ fix the displayed left and right steps; and the boundary row $B$ records whether the witness is closed, normal-source, atom-source, or substitution-boundary conditional before the join row is consumed as local evidence.

The structural rows $H,C,P,N$ only transport, replay, record provenance for, and locally name the same packet. Since the carrier has no coordinate for a closed Church--Rosser theorem, substitution compatibility, a closed parallel diamond, subject reduction, or quotient equality, the candidate join cannot export any of those objects.
\end{proof}

\begin{theorem}[MetaCIC local-diamond closedness-boundary classification]
\label{thm:metacic-local-diamond-witness-closedness-boundary-classification}
For every accepted $\MetaCICLocalDiamondWitnessUp$ carrier $W=(K,L,R,J,B,H,C,P,N)$, the boundary row $B$ must be displayed before any consumer reads the candidate-join row $J$. The displayed row classifies the witness as closed, normal-source, atom-source, or substitution-boundary conditional, and the later join read may only be interpreted inside that classification.

Consequently a local-diamond witness cannot turn a candidate join into arbitrary closed Church--Rosser, $\mathrm{BetaParallelSubstitutionCompatibility}$, $\mathrm{BetaParallelDiamondClosed}$, subject reduction, or quotient equality of terms.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-local-diamond-witness-carrier}. The carrier lists $B$ as the closedness and boundary row, while \autoref{thm:metacic-local-diamond-witness-candidate-join-exactness} already requires $J$ to be read only after the peak, branch, and boundary rows have been displayed.

Read $B$ before $J$. Its alternatives are closed, normal-source, atom-source, and substitution-boundary conditional, so the candidate common reduct in $J$ is consumed only under the exposed boundary case.

The structural rows $H,C,P,N$ transport, replay, source, and name the same classification. Since no row contains a closed Church--Rosser theorem, substitution compatibility, a closed parallel diamond, subject reduction, or quotient equality of terms, the candidate join remains a classified local witness rather than a global confluence claim.
\end{proof}

\closureat{MetaCICLocalDiamondWitnessUp}{seedStr}

\begin{closurestatus}{\MetaCICLocalDiamondWitnessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-local-diamond-witness-carrier} and \autoref{thm:metacic-local-diamond-witness-namecert-obligations} seed the finite local-diamond witness packet over peaks, branch steps, candidate joins, closedness boundaries, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close arbitrary closed Church--Rosser, BetaParallelSubstitutionCompatibility, BetaParallelDiamondClosed, subject reduction, quotient equality of terms, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, peak exposure, left-step and right-step evidence, candidate-join exactness, boundary classification, TasteGate nontriviality, FieldFaithful coverage, transport, replay, provenance, and local naming.}
  \constructivestory{A $\MetaCICLocalDiamondWitnessUp$ packet is generated from a local peak row, left-step row, right-step row, candidate-join row, closedness and boundary row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
