\chapter{A Concrete Naming Certificate for $\CauchyCompleteApartnessSpaceUp$}
\label{ch:concrete-instances-cauchy-complete-apartness-space-namecert}
\origin{human}

Following Bishop and Bridges on constructive apartness and completion, the $\CauchyCompleteApartnessSpaceUp$ packet records a displayed apartness space whose Cauchy data are complete by finite tolerance inspection. It sits after the located completion criterion of \autoref{ch:concrete-instances-located-completion-criterion-namecert}, the apartness completion boundary of \autoref{ch:concrete-instances-apartness-completion-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a constructive completion object for L10 Real and Completion consumers; it is not a quotient completion, a selected limit, a trichotomy principle, a countable-choice schedule, or a host real equality test.

\begin{definition}[Cauchy-complete apartness space carrier]
\label{def:cauchy-complete-apartness-space-carrier}
A $\CauchyCompleteApartnessSpaceUp$ carrier is a finite $\BHist$ packet
$$
A=(X,G,T,S,R,D,E,L,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the displayed apartness-space carrier, recording the points, positive separation evidence, and local apartness classifier inspected by the packet.
\item $G$ is the positive-gap row, carrying the finite apartness witnesses used to separate accepted Cauchy windows.
\item $T$ is the Cauchy tolerance route, recording the requested dyadic budgets and the finite window discipline that makes the Cauchy request inspectable.
\item $S$ is the $\StreamNameUp$ observation row for the Cauchy name.
\item $R$ is the $\RegSeqRatUp$ readback row extracted from the displayed windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, including radius, endpoint, and comparison rows used by the Cauchy and apartness checks.
\item $E$ is the terminal $\RealUp$ seal row available only after $S,R,D$ have been exposed.
\item $L$ is the $\LocatedCompletionCriterionUp$ row, recording the finite located-completion admission route for the same Cauchy data.
\item $Q$ is the $\ApartnessCompletionUp$ handoff row, recording the separated apartness-completion boundary read by completion-facing consumers.
\item $H$ records componentwise $\hsame$ transport for the apartness source, positive gap, Cauchy tolerance route, stream window, regular readback, dyadic ledger, Real seal, located-completion criterion, apartness-completion handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Cauchy-complete apartness-space request through $X,G,T,S,R,D,E,L,Q$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompleteApartnessSpaceUp$, $\LocatedCompletionCriterionUp$, $\ApartnessCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompleteApartnessSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,G,T,S,R,D,E,L,Q,H,C,P,N$. It has no coordinate for quotient Cauchy classes, chosen representatives, selected limits, countable choice, trichotomy, host real equality, or a host-level complete space.
\end{definition}

\begin{theorem}[Cauchy-complete apartness space NameCert obligations]
\label{thm:cauchy-complete-apartness-space-namecert-obligations}
For every accepted $\CauchyCompleteApartnessSpaceUp$ carrier $A=(X,G,T,S,R,D,E,L,Q,H,C,P,N)$, the local $\NameCert_{\CauchyCompleteApartnessSpaceUp}$ surface consists exactly of carrier admission for the apartness source, positive-gap witnesses, Cauchy tolerance route, finite stream windows, regular rational readback, dyadic tolerance ledger, terminal Real seal, located-completion criterion, apartness-completion handoff, componentwise transport, displayed continuation replay, package provenance, and local naming rows.

Every completion-facing consumer must read the finite route
$$
X,G,T\longmapsto S,R,D\longmapsto E\longmapsto L,Q\longmapsto H,C,P,N
$$
before treating the space as Cauchy complete for displayed apartness data.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-complete-apartness-space-carrier}. The rows $X,G,T$ expose the apartness source, positive separation witnesses, and the Cauchy tolerance route before any Real-facing or completion-facing row is available.

The finite readback then passes through $S,R,D$. Stream windows supply the observed name data, regular rational readback repacks those windows, and the dyadic ledger records the tolerance and comparison budgets used by both the Cauchy and apartness checks.

The terminal and completion rows are downstream. Row $E$ seals the Real-facing read, row $L$ records the located completion criterion route of \autoref{ch:concrete-instances-located-completion-criterion-namecert}, and row $Q$ records the apartness completion boundary of \autoref{ch:concrete-instances-apartness-completion-namecert}.

Finally $H,C,P,N$ transport, replay, source, and name only that displayed route. Since the carrier contains no quotient class, chosen representative, selected limit, countable-choice schedule, trichotomy row, host equality test, or host complete-space coordinate, those objects cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[Cauchy-complete apartness space located-completion handoff]
\label{thm:cauchy-complete-apartness-space-located-completion-handoff}
Every $\LocatedCompletionCriterionUp$, $\ApartnessCompletionUp$, or $\RealUp$ consumer of an accepted $\CauchyCompleteApartnessSpaceUp$ packet reaches the completion-facing surface only through the displayed apartness carrier $X$, positive-gap row $G$, Cauchy tolerance route $T$, finite $\StreamNameUp$ window $S$, $\RegSeqRatUp$ readback $R$, $\DyadicRatCoreUp$ tolerance ledger $D$, terminal $\RealUp$ seal $E$, located-completion row $L$, apartness-completion handoff $Q$, componentwise transport $H$, displayed replay $C$, provenance $P$, and local name $N$.

The handoff exports complete-apartness data only as finite NameCert rows. It does not export quotient completions, selected limits, countable choice, trichotomy, host real equality, or an ambient completeness theorem for all $\RealUp$ names.
\end{theorem}
\begin{proof}
Begin with a completion-facing or Real-facing consumer. Projection of the carrier gives the ordered route from the apartness source and positive gap rows through the Cauchy tolerance row, then through the finite stream and dyadic readback rows.

The located-completion handoff is forced through the existing siblings. The row $L$ is read as the located criterion route named in \autoref{thm:located-completion-criterion-namecert-obligations}, while $Q$ is read as the apartness-completion boundary named in \autoref{thm:apartness-completion-namecert-obligations}. Both are downstream of the same $S,R,D,E$ readback route.

Transport and replay cannot add coordinates. Rows $H,C,P,N$ preserve and name the same finite route, so a consumer receives complete-apartness evidence only through displayed BEDC rows and receives no quotient equality, selected representative, choice schedule, trichotomy decision, host equality test, or ambient completeness principle.
\end{proof}

\falsifiablePrediction{Every accepted $\CauchyCompleteApartnessSpaceUp$ consumer factors a completion-facing read through one apartness source row, one positive-gap row, one Cauchy tolerance route, one $\StreamNameUp$ window, one $\RegSeqRatUp$ readback, one $\DyadicRatCoreUp$ tolerance ledger, one $\RealUp$ seal, one $\LocatedCompletionCriterionUp$ row, one $\ApartnessCompletionUp$ handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{located-completion-criterion, apartness-completion, streamname, regseqrat, dyadicratcore, real: $\CauchyCompleteApartnessSpaceUp$ is not bijective to any listed sibling because it jointly carries apartness-source evidence, positive gaps, Cauchy tolerance inspection, finite readback, Real sealing, located-completion admission, apartness-completion handoff, transport, replay, provenance, and local naming as one completion packet.}

\closureat{CauchyCompleteApartnessSpaceUp}{seedStr}

\begin{closurestatus}{\CauchyCompleteApartnessSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-complete-apartness-space-carrier}, \autoref{thm:cauchy-complete-apartness-space-namecert-obligations}, and \autoref{thm:cauchy-complete-apartness-space-located-completion-handoff} seed the finite Cauchy-complete apartness-space route over apartness sources, positive gaps, Cauchy tolerance windows, regular readback, Real seals, located-completion criteria, apartness-completion handoffs, and local NameCert data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, apartness-source exactness, positive-gap visibility, Cauchy tolerance inspection, finite readback, Real seal handoff, located-completion criterion admission, apartness-completion handoff, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCompleteApartnessSpaceUp.}
  \constructivestory{A $\CauchyCompleteApartnessSpaceUp$ packet is generated from an apartness source row, positive-gap evidence, a Cauchy tolerance route, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealUp seal, a LocatedCompletionCriterion row, an ApartnessCompletion handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
