\chapter{A Concrete Naming Certificate for $\NestedIntervalCauchyUp$}
\label{ch:concrete-instances-nested-interval-cauchy-namecert}
\origin{human}

Following Bishop and Bridges on nested interval and Cauchy real constructions, the $\NestedIntervalCauchyUp$ packet records the finite route by which a displayed nested interval chain becomes a regular rational Cauchy name before the terminal real seal is available. It consumes the dyadic endpoint and comparison rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}, and the dyadic finite-tail handoff of \autoref{ch:concrete-instances-nested-dyadic-cauchy-namecert}. The packet is a textbook-grounded L10 completion route for interval evidence; it is not a completed intersection point, quotient real, host real equality, countable-choice selector, or ambient completeness principle.

\begin{definition}[Nested interval Cauchy carrier]
\label{def:nested-interval-cauchy-carrier}
A $\NestedIntervalCauchyUp$ carrier is a finite $\BHist$ packet
$$
K=(I,D,W,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite nested interval window. It records the inspected interval prefix, endpoint rows, containment rows, and nonempty-window evidence visible to the nested-interval consumer.
\item $D$ is the $\DyadicRatCoreUp$ endpoint and comparison ledger used to read endpoint order, diameter, and tolerance comparisons at the requested dyadic scales.
\item $W$ is the shrinking-width witness row. It assigns each displayed precision request to a prefix index whose interval diameter is bounded by the requested tolerance.
\item $S$ is the $\StreamNameUp$ schedule row. It names exactly the interval-prefix entries, endpoint observations, and diameter comparisons that may be opened before regular rational readback.
\item $R$ is the $\RegSeqRatUp$ handoff row formed from the scheduled endpoint or midpoint observations and the shrinking-width witness.
\item $E$ is the $\RealUp$ seal row reached only after $I,D,W,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for interval prefixes, dyadic ledgers, shrinking-width witnesses, stream schedules, regular rational readback, real seals, replay rows, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite nested-interval request through $D,W,S,R,E$ and then through the structural rows.
\item $P$ is the $\Pkg$ provenance over $\NestedIntervalCauchyUp$, $\NestedIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\NestedDyadicCauchyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedIntervalCauchyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these ten displayed rows. It has no coordinate for a completed intersection point, quotient real equality, host real equality, countable-choice selector, ambient completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Nested interval Cauchy NameCert obligations]
\label{thm:nested-interval-cauchy-namecert-obligations}
For every accepted $\NestedIntervalCauchyUp$ carrier
$$
K=(I,D,W,S,R,E,H,C,P,N),
$$
the local $\NameCert_{\NestedIntervalCauchyUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the nested interval prefix, dyadic endpoint ledger, shrinking-width witness, stream schedule, regular rational handoff, real seal, transport, replay, provenance, and local naming row;
\item prefix exposure, requiring each interval read to be one of the displayed rows of $I$;
\item endpoint and diameter exactness, requiring every endpoint-order and diameter comparison to be read through $D$;
\item precision discharge, requiring every Cauchy tolerance request to be answered by a prefix index and comparison stored in $W$;
\item schedule compatibility, requiring $S$ to expose only the interval-prefix, endpoint, and diameter observations used by $W$ and $R$;
\item $\RegSeqRatUp$ handoff, requiring $R$ to be formed only after the prefix, dyadic, width, and schedule rows have been projected;
\item $\RealUp$ seal nonescape, requiring $E$ to be consumed only after $R$ and the structural rows have fixed the finite route.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:nested-interval-cauchy-carrier}. The projection exposes one finite nested interval prefix, one dyadic endpoint ledger, one shrinking-width witness, one StreamName schedule, one RegSeqRat handoff, one Real seal, and the transport, replay, provenance, and naming rows.

Prefix exposure is forced by $I$. A consumer may inspect only interval rows already present in the finite prefix, and each such row carries the endpoint observations that the downstream dyadic ledger may compare.

Endpoint and diameter exactness are forced by $D$. Every order or diameter comparison used in the Cauchy route is a displayed dyadic comparison, so no external host interval relation is introduced.

Precision discharge is then forced by $W$. Each tolerance request names a displayed prefix index and a displayed comparison certifying that the selected interval is small enough for the requested regular rational read.

The schedule and handoff rows are downstream. The row $S$ records the finite prefix, endpoint, and diameter observations that may be opened, and $R$ repacks exactly those observations as regular rational Cauchy data.

Finally $E,H,C,P,N$ close the route. The Real seal is reachable only after the regular handoff has been displayed, while the structural rows only transport, replay, source, and name the same finite data. Therefore no completed intersection point, quotient real equality, host real equality, countable-choice selector, ambient completeness, Lean verification, or bridge-checking coordinate is present.
\end{proof}

\begin{theorem}[Nested interval Cauchy RegSeqRat handoff]
\label{thm:nested-interval-cauchy-regseqrat-handoff}
Let $K=(I,D,W,S,R,E,H,C,P,N)$ be an accepted $\NestedIntervalCauchyUp$ carrier. Every $\RegSeqRatUp$ consumer of $K$ factors through the finite route
$$
I
\longmapsto
D,W
\longmapsto
S
\longmapsto
R
\longmapsto
H,C,P,N .
$$
The route reads a finite nested interval prefix, displayed dyadic endpoint and diameter comparisons, a shrinking-width witness, and scheduled endpoint observations before it exports the regular rational Cauchy row.
\end{theorem}
\begin{proof}
Start with the displayed interval prefix $I$. Its rows give the only endpoint data available to a regular rational consumer, and the containment rows keep later prefix rows inside earlier rows.

Use the dyadic ledger $D$ and shrinking-width witness $W$ to answer a displayed Cauchy tolerance request. The selected prefix index, endpoint observations, and diameter comparison are part of the same finite packet, so no external modulus or choice of tail is needed.

The schedule row $S$ then fixes which interval endpoints or midpoint observations are opened. The handoff row $R$ is obtained by reading those scheduled observations under the width discipline and repacking them as the regular rational Cauchy surface.

The rows $H,C,P,N$ transport, replay, source, and name that handoff. Since the carrier has no additional tail selector, quotient-real coordinate, or completed intersection coordinate, every RegSeqRat read factors through the displayed route.
\end{proof}

\closureat{NestedIntervalCauchyUp}{seedStr}

\begin{closurestatus}{\NestedIntervalCauchyUp}
  \constructivestory{A $\NestedIntervalCauchyUp$ packet is generated from finite nested interval windows, dyadic endpoint and diameter ledgers, shrinking-width witnesses, StreamName schedules, RegSeqRat handoffs, a Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-interval-cauchy-carrier}, \autoref{thm:nested-interval-cauchy-namecert-obligations}, and \autoref{thm:nested-interval-cauchy-regseqrat-handoff} seed the finite nested interval Cauchy route from interval-prefix evidence to RegSeqRat readback and the Real seal boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close completed intersections, quotient real equality, host real equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, prefix exposure, endpoint and diameter exactness, precision discharge, schedule compatibility, RegSeqRat handoff, and Real seal nonescape for BEDC.Derived.NestedIntervalCauchyUp.}
\end{closurestatus}
