\chapter{A Concrete Naming Certificate for $\ContinuousImageCompactUp$}
\label{ch:concrete-instances-continuous-image-compact-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\ContinuousImageCompactUp$ packet records the finite-net reading of the image of a compact metric source under a displayed continuous map. It sits over the compact source of \autoref{ch:concrete-instances-compactmetric-namecert}, the graph and pointwise-continuity row of \autoref{ch:concrete-instances-continuousmap-namecert}, and the compact-uniform-continuity route of \autoref{ch:concrete-instances-compactuniformcontinuity-namecert}. The packet names the finite image-net certificate needed by downstream compactness and extreme-value consumers; it is not an open-cover compactness theorem, not a host image-set construction, and not a quotient equality principle for target names.

\begin{definition}[Continuous image compact carrier]
\label{def:continuous-image-compact-carrier}
A $\ContinuousImageCompactUp$ carrier is a finite $\BHist$ packet
$$
I=(K,F,U,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row. It exposes only the compact metric inspection data, finite source-net rows, source radii, and source $\NameCert$ provenance consumed by the image certificate.
\item $F$ is the $\ContinuousMapUp$ row from the source surface displayed by $K$ into the target metric surface. It records the graph, pointwise continuity data, and target readback boundary available to the packet.
\item $U$ is the $\CompactUniformContinuityUp$ row for $F$ over $K$. It turns each target tolerance request into a finite source-net radius before any image-net row is exported.
\item $E$ is the finite source-net ledger. It records the displayed source centers, the radius attached to the requested target tolerance, and the finite coverage row supplied by $K$.
\item $T$ is the finite target-image ledger. It records the target names $F(e)$ for each displayed source center $e$ in $E$ and the target tolerance justified through $U$.
\item $H$ records componentwise $\hsame$ transport for the compact source, continuous-map row, compact-uniform-continuity row, source-net ledger, target-image ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an image-compactness request through $K,F,U,E,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\ContinuousImageCompactUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\CompactUniformContinuityUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ContinuousImageCompactUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $K,F,U,E,T,H,C,P,N$. It has no coordinate for open-cover compactness, a host image subset, a selected inverse image, quotient equality of target names, or ambient completeness.
\end{definition}

\begin{theorem}[Continuous image compact NameCert obligations]
\label{thm:continuous-image-compact-namecert-obligations}
For every accepted $\ContinuousImageCompactUp$ carrier $I=(K,F,U,E,T,H,C,P,N)$, the local $\NameCert_{\ContinuousImageCompactUp}$ surface consists exactly of six finite obligation rows:
\begin{enumerate}
\item carrier admission for the compact source, continuous-map row, compact-uniform-continuity row, source-net ledger, target-image ledger, transport, replay, provenance, and local naming rows;
\item source-net accountability, requiring every displayed source center and radius in $E$ to be read through the compact metric row $K$;
\item continuity routing, requiring every target tolerance request to pass through the compact-uniform-continuity row $U$ for the continuous-map row $F$ before $T$ is exposed;
\item image-net exactness, requiring every target center in $T$ to be the displayed $F$-readback of a source center from $E$;
\item componentwise transport and replay stability under $H$ and $C$ for the same displayed rows;
\item ledger refusal, stating that open-cover compactness, host image sets, selected inverse images, quotient equality, and ambient completeness are not carrier coordinates.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The mathematical rows are $K,F,U,E,T$, and the structural rows are $H,C,P,N$.

The source-net obligation is read first. Row $E$ may display only centers and radii whose coverage data has already been supplied by the compact metric row $K$.

The continuity route is next. A target tolerance is sent through $U$, which supplies the source radius for the same displayed map row $F$ over the same compact source $K$.

The target-image ledger is therefore forced. Each target center in $T$ is obtained by reading $F$ at one of the displayed source centers in $E$, and the radius attached to that target center is the tolerance justified by $U$.

Transport, replay, provenance, and local naming preserve the row order. Since the excluded objects do not occur among $K,F,U,E,T,H,C,P,N$, no local obligation can export them.
\end{proof}

\begin{theorem}[Finite-net image compactness]
\label{thm:continuous-image-compact-finite-net-image}
Every accepted $\ContinuousImageCompactUp$ carrier $I=(K,F,U,E,T,H,C,P,N)$ exports compactness of the displayed image only as the finite target-net row $T$ obtained from the source-net row $E$ along the continuous-map row $F$ and the compact-uniform-continuity row $U$. A downstream compactness consumer receives the finite route
$$
\CompactMetricUp,\quad
\ContinuousMapUp,\quad
\CompactUniformContinuityUp,\quad
\ContinuousImageCompactUp
$$
and receives no open-cover compactness datum, host image subset, selected preimage, quotient equality of target names, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Begin with an image-compactness request at a target tolerance. By the obligation theorem, the request must pass through $U$ before the target-image ledger $T$ can be read.

The row $U$ supplies a source radius for the same map row $F$ over the same compact source $K$. The compact source row then exposes a finite source-net ledger $E$ at that radius.

Map the displayed source centers through $F$. The finite list of target readbacks is exactly the target-image ledger $T$, and the tolerance attached to it is the one already routed through $U$.

Rows $H,C,P,N$ transport, replay, package, and name this finite route without adding another coordinate. Thus the exported compactness content is the finite image-net row $T$ and not an open-cover, host-image, selected-preimage, quotient-equality, or completeness principle.
\end{proof}

\closureat{ContinuousImageCompactUp}{seedStr}

\begin{closurestatus}{\ContinuousImageCompactUp}
  \constructivestory{A $\ContinuousImageCompactUp$ packet is generated from a CompactMetricUp source row, a ContinuousMapUp row, a CompactUniformContinuityUp row, a finite source-net ledger, a finite target-image ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:continuous-image-compact-carrier}, \autoref{thm:continuous-image-compact-namecert-obligations}, and \autoref{thm:continuous-image-compact-finite-net-image} seed the finite-net image-compactness route from compact metric sources to downstream compactness consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, host image-set construction, selected preimages, quotient equality of target names, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-net accountability, continuity routing, image-net exactness, transport and replay stability, and local NameCert registration for BEDC.Derived.ContinuousImageCompactUp.}
\end{closurestatus}
