\chapter{A Concrete Naming Certificate for $\RieszSpaceUp$}
\label{ch:concrete-instances-riesz-space-namecert}
\origin{human}

Following Riesz and Kantorovich, the $\RieszSpaceUp$ packet records the finite BEDC naming surface for a real vector lattice with a displayed positive cone and norm-facing compatibility rows. It sits over the algebraic vector-space carrier of \autoref{ch:concrete-instances-vecspace-namecert}, the join-meet order rows of \autoref{ch:concrete-instances-lattice-namecert}, the norm comparison surface of \autoref{ch:concrete-instances-norm-namecert}, the positive scalar endpoint discipline of \autoref{ch:concrete-instances-positivereal-namecert}, and the real scalar seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the BEDC-facing ordered-functional-analysis object; it is not a host order primitive, a supremum completion theorem, a Banach-lattice completeness claim, or a choice of lattice decompositions outside the displayed finite ledger.

\begin{definition}[RieszSpace carrier]
\label{def:riesz-space-carrier}
A $\RieszSpaceUp$ carrier is a finite $\BHist$ packet
$$
R=(V,L,N,P,H,C,S)
$$
with the following displayed rows:
\begin{enumerate}
\item $V$ is the $\VecSpaceUp$ row naming the carried vector endpoint, real scalar endpoint, zero vector, addition, additive inverse, scalar action, and finite vector-space law ledger.
\item $L$ is the lattice row, recording join and meet operations on the same vector endpoint, the induced order-comparison rows, and the finite absorption, commutativity, associativity, and distributivity witnesses used by the local classifier.
\item $N$ is the norm or seminorm compatibility row, read through $\NormUp$, saying that the displayed norm endpoint respects the vector rows and the lattice decomposition rows already carried by $V$ and $L$.
\item $P$ is the positive-cone decomposition row, read through $\PositiveRealUp$ and $\RealUp$, recording positive and negative part formation, cone membership, scalar positivity, and the local identity route tying a vector to the difference of its displayed positive pieces.
\item $H$ records componentwise $\hsame$ transport for the vector-space rows, lattice join and meet rows, norm or seminorm rows, positive-cone rows, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a Riesz-space request through $V,L,N,P,H$ back to the same finite ordered vector-lattice surface.
\item $S$ is the $\Pkg$ provenance and local $\NameCert_{\RieszSpaceUp}$ row over $\RieszSpaceUp$, $\VecSpaceUp$, $\LatticeUp$, $\NormUp$, $\PositiveRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\end{enumerate}
The classifier compares accepted packets only through $V,L,N,P,H,C,S$. It has no coordinate for an ambient order relation, a host supremum construction, a selected order completion, Banach-lattice completeness, pointwise function models, or a quotient by order ideals.
\end{definition}

\begin{theorem}[RieszSpace NameCert obligations]
\label{thm:riesz-space-namecert-obligations}
For every accepted $\RieszSpaceUp$ carrier $R=(V,L,N,P,H,C,S)$, the local $\NameCert_{\RieszSpaceUp}$ surface consists exactly of carrier admission, vector-space row compatibility, lattice join and meet exactness, norm or seminorm compatibility, positive-cone decomposition, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, and local naming. A downstream consumer may read the common vector endpoint, the real scalar endpoint, the join and meet operations, the norm-facing comparison row, and the positive-cone ledger, but it receives no host order primitive, no chosen order completion, no Banach-lattice completeness theorem, and no pointwise function representation.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:riesz-space-carrier}. The packet displays exactly the vector-space row $V$, the lattice row $L$, the norm or seminorm compatibility row $N$, the positive-cone decomposition row $P$, and the structural rows $H,C,S$.

The vector-space obligations are inherited from the carried $\VecSpaceUp$ row, while the lattice obligations are read only through the displayed join and meet ledger. Thus the same vector endpoint is the domain of addition, scalar multiplication, join, meet, and order comparison.

The norm-facing and positive-cone obligations are finite rows. The row $N$ records compatibility with the vector and lattice decompositions, and $P$ records positive and negative part formation using the $\PositiveRealUp$ and $\RealUp$ scalar seals.

Finally $H,C,S$ transport, replay, source, and locally certify only the displayed coordinates. Since the carrier has no ambient order coordinate, no completion selector, no Banach-lattice completeness row, and no pointwise function model, none of those objects can be exported by the local certificate.
\end{proof}

\begin{theorem}[RieszSpace lattice-norm compatibility]
\label{thm:riesz-space-lattice-norm-compatibility}
If two accepted $\RieszSpaceUp$ packets are related by the classifier, then their vector-space rows, lattice join and meet rows, norm or seminorm compatibility rows, and positive-cone decomposition rows are related by the componentwise $\hsame$ transport recorded in $H$. Consequently every downstream norm-facing or order-facing read factors through the displayed vector-lattice ledger and never through a host order equality or a hidden normed-lattice quotient.
\end{theorem}
\begin{proof}
Unfold the classifier of \autoref{def:riesz-space-carrier}. Its comparison coordinates are exactly the vector-space row, lattice join and meet row, norm or seminorm compatibility row, positive-cone row, replay row, provenance row, and local naming row.

The vector component transports through the $\VecSpaceUp$ comparison, and the lattice component transports through the displayed join and meet comparisons. The norm or seminorm row then moves along the same transported vector and lattice data.

The positive-cone row is carried componentwise as well: positive part, negative part, cone membership, scalar positivity, and reconstruction of the original vector all remain inside the visible ledger. Hence every norm-facing or order-facing consumer reads a transported finite certificate, not a host order equality or a hidden quotient construction.
\end{proof}

\closureat{RieszSpaceUp}{seedStr}

\begin{closurestatus}{\RieszSpaceUp}
  \constructivestory{A $\RieszSpaceUp$ packet is generated from vector-space rows, lattice join and meet rows, norm or seminorm compatibility rows, positive-cone decomposition data, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riesz-space-carrier}, \autoref{thm:riesz-space-namecert-obligations}, and \autoref{thm:riesz-space-lattice-norm-compatibility} seed the finite ordered vector-lattice certificate over VecSpaceUp, LatticeUp, NormUp, PositiveRealUp, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host order primitives, supremum completion, Banach-lattice completeness, pointwise function representation, quotient by order ideals, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, vector-space compatibility, lattice join and meet exactness, norm or seminorm compatibility, positive-cone decomposition, transport, replay, provenance, and local naming for BEDC.Derived.RieszSpaceUp.}
\end{closurestatus}
