\chapter{A Concrete Naming Certificate for $\DedekindRealUp$}
\label{ch:concrete-instances-dedekind-real-namecert}
\origin{human}

Following Dedekind and Bishop--Bridges constructive analysis, the $\DedekindRealUp$ packet records a real name by a displayed located cut together with the finite Cauchy readback surface that lets completion-facing consumers compare cut data with regular rational Cauchy names. It sits beside the located-cut carrier of \autoref{ch:concrete-instances-locatedcut-namecert}, the tight cut boundary of \autoref{ch:concrete-instances-tight-located-cut-namecert}, the regular rational sequence route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the cut-versus-Cauchy comparison surface; it is not a quotient of cuts, a selected supremum, trichotomy on rationals, countable choice, or an ambient completeness theorem for $\RealUp$.

\begin{definition}[DedekindReal carrier]
\label{def:dedekind-real-carrier}
A $\DedekindRealUp$ carrier is a finite $\BHist$ packet
$$
D=(L,C,T,R,S,Q,E,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LocatedCutUp$ row exposing the lower and upper rational probes and the locatedness witness available to the cut.
\item $C$ is the $\CauchyCutUp$ row tying finite Cauchy windows to the same cut boundary.
\item $T$ is the $\TightLocatedCutUp$ row recording the no-gap compatibility between lower and upper probes.
\item $R$ is the $\RegSeqRatUp$ regular rational sequence row used as the Cauchy name readback.
\item $S$ is the $\StreamNameUp$ finite-window row selecting the inspected rational approximants.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare cut probes and Cauchy windows at one displayed budget.
\item $E$ is the terminal $\RealUp$ seal row reached only after $L,C,T,R,S,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for cut, Cauchy-cut, tightness, sequence, stream, tolerance, Real-seal, replay, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay from a cut-facing or Cauchy-facing request through $L,C,T,R,S,Q$ and then to $E$.
\item $P$ is the $\Pkg$ provenance over $\DedekindRealUp$, $\LocatedCutUp$, $\CauchyCutUp$, $\TightLocatedCutUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for quotient cut equality, a selected supremum, a detached Cauchy limit, rational trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{definition}
\leanchecked{BEDC.Derived.DedekindRealUp.DedekindRealTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DedekindReal NameCert obligations]
\label{thm:dedekind-real-namecert-obligations}
For every accepted $\DedekindRealUp$ carrier $D=(L,C,T,R,S,Q,E,H,K,P,N)$, the local $\NameCert_{\DedekindRealUp}$ surface consists exactly of carrier admission for the displayed packet, located-cut exposure through $L$, Cauchy-cut compatibility through $C$, tight no-gap checking through $T$, regular rational readback through $R$, finite stream-window exposure through $S$, dyadic tolerance comparison through $Q$, terminal $\RealUp$ sealing through $E$, componentwise transport through $H$, displayed replay through $K$, provenance through $P$, and local naming through $N$.

Every Real and Completion consumer that treats a Dedekind-style cut as a real name must read the finite route
$$
\LocatedCutUp \longrightarrow \CauchyCutUp \longrightarrow \TightLocatedCutUp \longrightarrow \RegSeqRatUp \longrightarrow \StreamNameUp \longrightarrow \DyadicRatCoreUp \longrightarrow \RealUp
$$
before exporting any real-facing row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dedekind-real-carrier}. The accepted packet exposes only the located cut, Cauchy-cut, tightness, regular rational sequence, stream window, dyadic tolerance, Real seal, transport, replay, provenance, and local naming rows.

The cut side is forced by $L,C,T$. Locatedness supplies rational probes on both sides of the boundary, the Cauchy-cut row ties those probes to finite Cauchy windows, and the tight row records that no displayed gap remains between the lower and upper faces.

The Cauchy side is forced by $R,S,Q,E$. The regular rational sequence supplies the finite approximants, the stream row selects the inspected windows, the dyadic ledger fixes the comparison budget, and the Real seal can be reached only after those rows have been consumed.

Finally $H,K,P,N$ exhaust the structural surface. They transport, replay, source, and name the displayed rows only, so quotient cut equality, selected suprema, detached limits, rational trichotomy, countable choice, and ambient Real completeness have no export coordinate in the local certificate.
\end{proof}

\begin{theorem}[DedekindReal cut--Cauchy comparison]
\label{thm:dedekind-real-cut-cauchy-comparison}
Let $D=(L,C,T,R,S,Q,E,H,K,P,N)$ be an accepted $\DedekindRealUp$ carrier. A cut-facing read and a Cauchy-facing read compare only when both are routed through the same tolerance ledger $Q$ and the same terminal $\RealUp$ seal $E$. In particular, every admitted comparison between the Dedekind cut surface and the regular Cauchy real-name surface factors through
$$
(L,C,T) \longmapsto Q \longleftarrow (R,S)
$$
and then through $E,H,K,P,N$.

The comparison contains no quotient of cuts, no selected supremum, no selected Cauchy limit, no trichotomy branch, no countable-choice selector, and no appeal to ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the accepted packet. A cut-facing read can inspect only $L,C,T$, while a Cauchy-facing read can inspect only $R,S$ before the common dyadic tolerance row is reached.

The row $Q$ is the only displayed comparison budget. Therefore a lower-or-upper rational probe from $L$ and a regular rational approximant from $R,S$ can be compared only after both sides have entered the same dyadic ledger.

The terminal seal $E$ is downstream of that shared ledger. Transport and replay through $H$ and $K$ preserve the same order, and $P,N$ package only the resulting finite route.

Since no carrier coordinate stores quotient cut equality, a supremum selector, a detached limit, trichotomy, countable choice, or ambient completeness, the comparison is exactly the finite cut-versus-Cauchy route displayed above.
\end{proof}

\falsifiablePrediction{Every accepted $\DedekindRealUp$ consumer that claims a cut-versus-Cauchy real-name comparison must exhibit locatedcut, cauchycut, tightlocatedcut, regseqrat, streamname, dyadicratcore, real, transport, replay, provenance, and local namecert rows. A consumer omitting any one of those rows refutes the packet.}

\independenceWitness{locatedcut, cauchycut, tightlocatedcut, regseqrat, streamname, dyadicratcore, real: no listed sibling supplies the whole packet $D=(L,C,T,R,S,Q,E,H,K,P,N)$, because each sibling contributes only cut probes, Cauchy compatibility, tightness, rational sequence data, finite windows, tolerance budgets, or terminal real sealing while this chapter binds them as one finite comparison certificate.}

\closureat{DedekindRealUp}{seedStr}

\begin{closurestatus}{\DedekindRealUp}
  \constructivestory{A $\DedekindRealUp$ packet is generated from a LocatedCut row, CauchyCut compatibility row, TightLocatedCut no-gap row, RegSeqRat readback, StreamName finite windows, DyadicRatCore tolerance ledger, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-real-carrier}, \autoref{thm:dedekind-real-namecert-obligations}, and \autoref{thm:dedekind-real-cut-cauchy-comparison} seed the finite cut-versus-Cauchy real-name route from located cut probes through Cauchy compatibility, tightness, regular rational readback, finite stream windows, dyadic tolerance, and terminal Real sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient cut equality, selected suprema, selected Cauchy limits, rational trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-cut exposure, Cauchy-cut compatibility, tight no-gap checking, regular rational readback, finite-window exposure, dyadic tolerance comparison, terminal Real seal routing, and ledger nonescape for BEDC.Derived.DedekindRealUp.}
\end{closurestatus}
