\chapter{A Concrete Naming Certificate for $\DyadicSandwichUp$}
\label{ch:concrete-instances-dyadic-sandwich-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\DyadicSandwichUp$ packet records the finite squeeze surface by which lower and upper dyadic rows trap a regular rational tail before a Real-facing consumer can read the seal. It sits over the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tail ball boundary of \autoref{ch:concrete-instances-dyadic-tail-ball-namecert}, and the terminal Real packet of \autoref{ch:concrete-instances-real-namecert}. The packet names the squeeze route as finite certificate data; it is not a quotient-real equality theorem, a selected limit, trichotomy, or ambient $\RealUp$ completeness claim.

\begin{definition}[DyadicSandwich carrier]
\label{def:dyadic-sandwich-carrier}
A $\DyadicSandwichUp$ carrier is a finite $\BHist$ packet
$$
Q=(L,U,S,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the lower dyadic row, listing the inspected lower endpoints and their finite-window order witnesses.
\item $U$ is the upper dyadic row, listing the inspected upper endpoints and the matching containment witnesses.
\item $S$ is the $\StreamNameUp$ schedule row exposing only the windows on which $L$ and $U$ are compared.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger that records the dyadic radii, order comparisons, and residual budgets for the sandwich.
\item $R$ is the $\RegSeqRatUp$ regular-tail row whose displayed values remain between the lower and upper dyadic rows at the scheduled windows.
\item $H$ records componentwise $\hsame$ transport for lower rows, upper rows, schedules, dyadic ledgers, regular tails, replay rows, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from the dyadic lower and upper rows through the schedule, tolerance ledger, regular tail, and Real-facing handoff.
\item $P$ is the $\Pkg$ provenance over $\DyadicSandwichUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicTailBallUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicSandwichUp}$ row.
\end{enumerate}
The classifier reads accepted packets only through $L,U,S,D,R,H,C,P,N$. It has no coordinate for quotient equality of regular names, selected limits, trichotomy, countable choice, or an ambient completeness principle for $\RealUp$.
\end{definition}

\begin{theorem}[DyadicSandwich NameCert obligations]
\label{thm:dyadic-sandwich-namecert-obligations}
For every accepted $\DyadicSandwichUp$ carrier $Q=(L,U,S,D,R,H,C,P,N)$, the local $\NameCert_{\DyadicSandwichUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the lower dyadic row, upper dyadic row, StreamName schedule, DyadicRatCore tolerance ledger, RegSeqRat regular-tail row, transport, replay, provenance, and local naming;
\item lower/upper order, requiring each displayed lower row to lie below the matching upper row through the dyadic comparison data in $D$;
\item tail containment, requiring the regular-tail values in $R$ to remain inside the displayed dyadic interval at every window named by $S$;
\item classifier stability, requiring any accepted comparison of packets to transport $L,U,S,D,R,H,C,P,N$ componentwise and to preserve the displayed containment route;
\item squeeze handoff, requiring every $\DyadicTailBallUp$ or $\RealUp$ consumer to read the schedule, dyadic ledger, and regular-tail row before the terminal seal is available;
\item provenance exhaustion, requiring all accepted reads to be sourced by $P$ and locally named by $N$, with no hidden quotient, selected-limit, trichotomy, countable-choice, or ambient-completeness coordinate.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-sandwich-carrier}. The visible coordinates are exactly $L,U,S,D,R,H,C,P,N$, so carrier admission and provenance exhaustion are read from those rows.

The order and containment obligations are the two analytic faces of the same displayed dyadic ledger. The lower and upper rows are compared through $D$, while the regular-tail row $R$ is inspected only at windows named by $S$.

Classifier stability follows componentwise through $H$ and by replay through $C$. Since the replay route names the same lower row, upper row, schedule, dyadic ledger, and regular tail after transport, a classifier comparison cannot replace the sandwich with a quotient class or a selected limiting object.

Finally the consumer handoff is downstream of $S,D,R$. A $\DyadicTailBallUp$ or $\RealUp$ read therefore reaches the terminal boundary only after the finite squeeze rows have been displayed, and the carrier list supplies no trichotomy, countable-choice, or ambient-completeness datum.
\end{proof}

\begin{theorem}[DyadicSandwich regular Cauchy squeeze route]
\label{thm:dyadic-sandwich-regular-cauchy-squeeze-route}
Every $\RealUp$-facing read from an accepted $\DyadicSandwichUp$ packet factors through
$$
\DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \DyadicTailBallUp \longrightarrow \RealUp .
$$
The route first reads the dyadic lower and upper endpoints with their tolerance ledger, then the finite schedule, then the regular-tail row, then the dyadic tail-ball boundary, and only then the Real seal. It exports no quotient equality, selected limit, trichotomy, countable-choice principle, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start from an accepted packet $Q=(L,U,S,D,R,H,C,P,N)$. The dyadic information is exhausted by $L,U,D$, so every lower/upper comparison and tolerance request is first reduced to the $\DyadicRatCoreUp$ ledger.

The schedule row $S$ fixes the finite windows on which the squeeze is inspected. The regular-tail row $R$ is attached to those windows, so a consumer cannot read a tail value outside the displayed schedule.

The dyadic tail-ball boundary is then obtained by replaying the same lower, upper, schedule, dyadic-ledger, and regular-tail rows through $C$ and transporting them through $H$. The provenance row $P$ and local naming row $N$ package that route for the terminal $\RealUp$ read.

No remaining carrier coordinate can supply quotient equality, a selected limit, trichotomy, countable choice, or ambient completeness. Hence every Real-facing read factors through the displayed constructive squeeze route.
\end{proof}

\closureat{DyadicSandwichUp}{seedStr}

\begin{closurestatus}{\DyadicSandwichUp}
  \constructivestory{A $\DyadicSandwichUp$ packet is generated from a lower dyadic row, an upper dyadic row, a finite StreamName schedule, a DyadicRatCore tolerance ledger, a RegSeqRat regular-tail row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-sandwich-carrier}, \autoref{thm:dyadic-sandwich-namecert-obligations}, and \autoref{thm:dyadic-sandwich-regular-cauchy-squeeze-route} seed the constructive finite squeeze route from dyadic tail windows to Real-facing reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, lower/upper order, tail containment, classifier stability, squeeze handoff, and provenance exhaustion for BEDC.Derived.DyadicSandwichUp.}
\end{closurestatus}
