\chapter{A Concrete Naming Certificate for $\ObservableDiameterDecayUp$}
\label{ch:concrete-instances-observable-diameter-decay-namecert}
\origin{ai}

The $\ObservableDiameterDecayUp$ packet realizes the compact finite-net and uniform-modulus route of \autoref{ch:visions-compact-uniform-continuity} as a finite diameter ledger. It consumes the compact source of \autoref{ch:concrete-instances-compactmetric-namecert}, the pointwise graph and radius data of \autoref{ch:concrete-instances-continuousmap-namecert}, the finite radius ledger of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the source-to-target triangle estimate of \autoref{ch:concrete-instances-metric-triangle-uniform-estimate-namecert}. The packet exposes observable diameter decay as NameCert data rather than as a narrative compactness bridge.

\begin{definition}[Observable diameter decay carrier]
\label{def:observable-diameter-decay-carrier}
An $\ObservableDiameterDecayUp$ carrier is a finite $\BHist$ packet
$$
O=(K,F,L,T,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ finite-net source row, including the inspected centers and source-radius windows.
\item $F$ is the $\ContinuousMapUp$ pointwise graph and local-modulus row for the displayed map on those centers.
\item $L$ is the $\FiniteLebesgueNumberUp$ radius row binding the finite compact cover to one positive radius ledger.
\item $T$ is the $\MetricTriangleUniformEstimateUp$ triangle row that turns source-radius bounds and pointwise target estimates into a target-diameter bound.
\item $M$ is the $\UniformModulusUp$ handoff row, read only after $K,F,L,T$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for compact-net, continuous-map, radius-ledger, triangle-estimate, uniform-modulus, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from finite-net source windows through pointwise estimates, the finite Lebesgue-number row, the triangle estimate, and the uniform-modulus handoff.
\item $P$ is the $\Pkg$ provenance over $\ObservableDiameterDecayUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\FiniteLebesgueNumberUp$, $\MetricTriangleUniformEstimateUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ObservableDiameterDecayUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,F,L,T,M,H,C,P,N$. It has no coordinate for open-cover compactness, host semantic continuity, selected centers outside the displayed finite net, or ambient completeness.
\end{definition}

\begin{theorem}[Observable diameter decay NameCert obligations]
\label{thm:observable-diameter-decay-namecert-obligations}
For every accepted $\ObservableDiameterDecayUp$ carrier $O=(K,F,L,T,M,H,C,P,N)$, the local $\NameCert_{\ObservableDiameterDecayUp}$ surface consists exactly of carrier admission; compact finite-net coverage through $K$; pointwise-modulus compatibility through $F$; finite Lebesgue-number radius exactness through $L$; triangle-estimate diameter control through $T$; uniform-modulus handoff through $M$; componentwise transport and displayed replay through $H$ and $C$; and provenance exhaustion through $P$ and $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:observable-diameter-decay-carrier}. The visible coordinates are exactly the compact finite-net row, continuous-map row, finite radius ledger, triangle estimate, uniform-modulus handoff, and structural rows.

Coverage is read from $K$, and pointwise-modulus compatibility is read from $F$. The finite Lebesgue-number row $L$ binds those local source-radius windows to a single positive radius ledger.

The triangle row $T$ converts the shared source-radius bound and pointwise target estimates into the displayed target-diameter control. The uniform-modulus row $M$ is downstream from $K,F,L,T$, so the handoff cannot be inspected before the finite diameter-decay route is exposed.

Transport and replay through $H$ and $C$ preserve exactly those rows, while $P$ and $N$ source and name them. Since the carrier contains no open-cover compactness, host semantic continuity, external center selector, or ambient completeness coordinate, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Observable diameter decay compact-uniform route]
\label{thm:observable-diameter-decay-compact-uniform-route}
Every $\UniformModulusUp$ read from an accepted $\ObservableDiameterDecayUp$ packet factors through the finite route
$$
\CompactMetricUp \longrightarrow \ContinuousMapUp \longrightarrow \FiniteLebesgueNumberUp \longrightarrow \MetricTriangleUniformEstimateUp \longrightarrow \UniformModulusUp .
$$
The route measures diameter decay on displayed compact-net cells, transports pointwise target estimates along the finite Lebesgue-number radius row, and seals the result as a uniform-modulus handoff. It exports no open-cover compactness, host semantic continuity, selected center outside the packet, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with an accepted packet $O=(K,F,L,T,M,H,C,P,N)$. The compact source data are exactly the finite-net centers and source-radius windows recorded in $K$.

Read the continuous-map row $F$ at those displayed centers. These pointwise target estimates are tied to the same finite source windows that the compact-net row exposes.

The radius row $L$ supplies the finite Lebesgue-number ledger needed to make the source-radius request uniform over the inspected compact-net cells. The triangle row $T$ then turns the source bounds and pointwise target estimates into a target-diameter bound.

Only after that route is replayed through $C$ and transported through $H$ can the uniform-modulus handoff $M$ be read. The provenance and naming rows $P,N$ package the same route, and no carrier coordinate supplies open-cover compactness, host semantic continuity, external center selection, or ambient completeness.
\end{proof}

\falsifiablePrediction{Removing the $\FiniteLebesgueNumberUp$ radius row from an accepted $\ObservableDiameterDecayUp$ carrier breaks the $\UniformModulusUp$ handoff, because the compact finite-net source row and pointwise $\ContinuousMapUp$ estimates no longer share one displayed positive-radius ledger.}

\independenceWitness{compactuniformcontinuity, finitelebesguenumber, metrictriangleuniformestimate, uniformmodulus, compactmetric: none is bijective to $\ObservableDiameterDecayUp$ because this packet jointly carries compact-net coverage, pointwise continuous-map estimates, the finite Lebesgue-number radius ledger, triangle-estimate diameter control, uniform-modulus handoff, transport, replay, provenance, and local naming in one carrier.}

\closureat{ObservableDiameterDecayUp}{seedStr}

\begin{closurestatus}{\ObservableDiameterDecayUp}
  \constructivestory{An $\ObservableDiameterDecayUp$ packet is generated from a CompactMetric finite-net row, a ContinuousMap pointwise-modulus row, a FiniteLebesgueNumber radius ledger, a MetricTriangleUniformEstimate diameter-control row, a UniformModulus handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:observable-diameter-decay-carrier}, \autoref{thm:observable-diameter-decay-namecert-obligations}, and \autoref{thm:observable-diameter-decay-compact-uniform-route} seed the finite compact-net diameter-decay route consumed by uniform-modulus reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, host semantic continuity, selected centers outside the displayed finite net, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net coverage, pointwise-modulus compatibility, finite radius exactness, triangle-estimate diameter control, uniform-modulus handoff, transport and replay stability, and provenance exhaustion for BEDC.Derived.ObservableDiameterDecayUp.}
\end{closurestatus}
