\chapter{A Concrete Naming Certificate for $\BoundedRealIntervalPartitionUp$}
\label{ch:concrete-instances-bounded-real-interval-partition-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and the Riemann--Darboux treatment of bounded intervals, the $\BoundedRealIntervalPartitionUp$ packet records a finite subdivision surface for a displayed bounded $\RealUp$ interval. It sits after the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite StreamName windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the located partition surface of \autoref{ch:concrete-instances-located-real-interval-partition-namecert}. The packet supplies a reusable finite subdivision carrier for $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, and $\RegulatedIntegralUp$ consumers; it does not supply open-cover compactness, selected limits, quotient real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Bounded real interval partition carrier]
\label{def:bounded-real-interval-partition-carrier}
A $\BoundedRealIntervalPartitionUp$ carrier is a finite $\BHist$ packet
$$
B=(E,S,M,T,Q,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the bounded interval endpoint row, carrying lower and upper $\RealUp$ endpoint seals together with the finite $\StreamNameUp$ windows and $\RegSeqRatUp$ readbacks used to observe them.
\item $S$ is the ordered subdivision row, listing finitely many subdivision nodes between the displayed endpoints and the adjacent cell ledger they generate.
\item $M$ is the dyadic mesh-bound row, read through $\DyadicRatCoreUp$, recording a rational precision budget, finite cell-width bounds, and the endpoint-to-cell comparison rows.
\item $T$ is the tag-window row, assigning each cell a finite tag window and recording only the displayed containment evidence for that tag.
\item $Q$ is the regular rational readback row for the subdivision nodes, tag windows, mesh bounds, and endpoint comparisons.
\item $R$ is the terminal $\RealUp$ seal row for the endpoint and subdivision observations, reached only after $E,S,M,T,Q$ have been displayed.
\item $L$ is the integration-consumer ledger, recording that $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, and $\RegulatedIntegralUp$ consumers may read the finite partition only through the rows $E,S,M,T,Q,R$.
\item $H$ records componentwise $\hsame$ transport for endpoints, subdivision nodes, dyadic mesh bounds, tag windows, regular readbacks, real seals, consumer ledgers, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from endpoint observations to ordered cells, from cells to tag windows, and from mesh bounds to the consumer ledger.
\item $P$ is the $\Pkg$ provenance over $\BoundedRealIntervalPartitionUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, $\RegulatedIntegralUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BoundedRealIntervalPartitionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only by the displayed endpoint, subdivision, mesh-bound, tag-window, readback, seal, consumer-ledger, transport, replay, provenance, and local naming rows. It has no coordinate for an open-cover compactness proof, selected limiting partition, quotient real equality, host interval partition, countable choice, or ambient real-completeness principle.
\end{definition}

\begin{theorem}[Bounded real interval partition NameCert obligations]
\label{thm:bounded-real-interval-partition-namecert-obligations}
For every accepted $\BoundedRealIntervalPartitionUp$ carrier $B=(E,S,M,T,Q,R,L,H,C,P,N)$, the local $\NameCert_{\BoundedRealIntervalPartitionUp}$ surface consists exactly of carrier admission; bounded endpoint exposure through $E$; ordered subdivision exposure through $S$; dyadic mesh-bound exposure through $M$; tag-window containment through $T$; $\RegSeqRatUp$ readback through $Q$; terminal $\RealUp$ sealing through $R$; integration-consumer routing through $L$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $C$; $\Pkg$ provenance through $P$; and local naming through $N$.

Thus a Riemann, Darboux, Riemann--Stieltjes, or regulated-integral consumer receives a finite subdivision surface only after the endpoint, cell, mesh-bound, tag-window, readback, and seal rows have all been displayed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bounded-real-interval-partition-carrier}. The tuple lists the only available rows: endpoints, ordered subdivision nodes, dyadic mesh bounds, tag windows, regular readbacks, real seals, consumer routing, transport, replay, provenance, and local naming.

The endpoint stage is $E$. Its $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, and $\RealUp$ seals supply bounded endpoint observations before a cell can be inspected.

The finite subdivision stage is $S,M,T,Q$. The ordered row $S$ supplies the cells, the dyadic row $M$ records the mesh budget and cell-width bounds, the tag row $T$ confines each tag to a displayed window, and the regular readback row $Q$ reads those finite observations.

The consumer stage is $R,L,H,C,P,N$. The terminal seal $R$ is reached only through the displayed rows, while $L$ records the permitted $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, and $\RegulatedIntegralUp$ reads. The structural rows transport, replay, package, and name exactly this route, so the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bounded real interval partition mesh consumer readiness]
\label{thm:bounded-real-interval-partition-mesh-consumer-readiness}
Let $B=(E,S,M,T,Q,R,L,H,C,P,N)$ be an accepted $\BoundedRealIntervalPartitionUp$ carrier. The ordered subdivision row $S$ and dyadic mesh row $M$ are read as a bounded refinement of the located partition surface of \autoref{ch:concrete-instances-located-real-interval-partition-namecert} before any $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, or $\RegulatedIntegralUp$ consumer may inspect the integration-consumer ledger $L$. The consumer therefore receives a located finite partition with bounded dyadic mesh evidence, not an isolated mesh code or host interval partition.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bounded-real-interval-partition-carrier}. The endpoint row $E$ supplies the bounded Real interval, and the subdivision row $S$ lists ordered cells over that same endpoint surface.

Apply \autoref{thm:bounded-real-interval-partition-namecert-obligations}. The dyadic mesh-bound row $M$ is not a separate object; it is read after $S$ and compares adjacent cells by the displayed $\DyadicRatCoreUp$ budget.

The located partition dependency is therefore substantive. The rows $S$ and $M$ refine the located interval partition of \autoref{ch:concrete-instances-located-real-interval-partition-namecert} by adding bounded endpoint access and dyadic mesh bounds before the regular readback $Q$ and real seal $R$ are exposed.

Only then may the ledger $L$ route the packet to Riemann, Darboux, Riemann--Stieltjes, or regulated-integral consumers. Since the carrier contains no host partition coordinate, every such consumer reads the bounded refinement route rather than a free-standing subdivision code.
\end{proof}

\begin{theorem}[Bounded real interval partition transport stability]
\label{thm:bounded-real-interval-partition-transport-stability}
Let $B=(E,S,M,T,Q,R,L,H,C,P,N)$ and $B'=(E',S',M',T',Q',R',L',H',C',P',N')$ be accepted $\BoundedRealIntervalPartitionUp$ carriers classified together by componentwise $\hsame$ transport. If $S'$ is read as the transported ordered subdivision over the transported bounded endpoint row $E'$, then the mesh-bound row, tag-window row, regular readback row, real-seal row, and integration-consumer ledger are all read through the same finite transported subdivision route.

The transported carrier therefore preserves the finite partition surface without adding open-cover compactness, selected limits, quotient real equality, a host interval partition, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the endpoint row. Componentwise transport carries $E$ to $E'$, including the finite StreamName windows, RegSeqRat readbacks, and Real seals attached to the lower and upper endpoints.

Read the transported subdivision through $S'$. Since its cells are displayed over $E'$, every later mesh or tag read remains attached to the same bounded interval route.

The rows $M',T',Q',R'$ are downstream of that route. The dyadic mesh bounds compare transported adjacent cells, the tag windows remain cell-local, the regular readbacks observe only the displayed finite windows, and the Real seal is reached after those observations.

Finally $L',H',C',P',N'$ carry the same route to the integration consumers and name it. No additional coordinate exists in the carrier, so the transported packet cannot export any of the excluded compactness, selection, quotient, host-partition, choice, or completeness data.
\end{proof}

\begin{theorem}[Bounded real interval partition consumer nonescape]
\label{thm:bounded-real-interval-partition-consumer-nonescape}
Every $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, or $\RegulatedIntegralUp$ consumer of an accepted $\BoundedRealIntervalPartitionUp$ packet receives only the finite route
$$
\StreamNameUp,\RegSeqRatUp,\DyadicRatCoreUp,\RealUp
\longmapsto
\BoundedRealIntervalPartitionUp .
$$
The route exposes endpoint rows, ordered subdivision rows, dyadic mesh bounds, tag windows, readbacks, terminal seals, componentwise transport, displayed replay, provenance, and local naming. It exports no open-cover compactness theorem, selected limiting partition, quotient real equality, host interval partition, measure-completion object, or ambient real-completeness principle.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bounded-real-interval-partition-namecert-obligations}. It makes $E,S,M,T,Q,R,L,H,C,P,N$ the entire public surface of the packet.

Apply \autoref{thm:bounded-real-interval-partition-transport-stability}. Any transported or refined consumer read must preserve the same endpoint-to-subdivision-to-mesh route before the consumer ledger $L$ is available.

Now inspect the consumers named in $L$. A Riemann or Darboux read may use the displayed cells and mesh bounds; a Riemann--Stieltjes read may additionally pair those cells with its own integrator row; and a regulated-integral read may use the same finite subdivision as a step surface. In each case the consumer receives only the listed finite rows and their structural provenance.

Since the carrier contains no row for compactness, selected limits, quotient equality, host partitions, measure completion, or ambient real completeness, none of those objects can escape through the consumer route.
\end{proof}

\closureat{BoundedRealIntervalPartitionUp}{seedStr}

\begin{closurestatus}{\BoundedRealIntervalPartitionUp}
  \constructivestory{A $\BoundedRealIntervalPartitionUp$ packet is generated from bounded Real endpoint seals, ordered subdivision rows, dyadic mesh bounds, tag windows, RegSeqRat readbacks, integration-consumer routing, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bounded-real-interval-partition-carrier}, \autoref{thm:bounded-real-interval-partition-namecert-obligations}, \autoref{thm:bounded-real-interval-partition-transport-stability}, and \autoref{thm:bounded-real-interval-partition-consumer-nonescape} seed the bounded real interval partition boundary over $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RiemannIntegralUp$, $\DarbouxIntegralUp$, $\RiemannStieltjesUp$, and $\RegulatedIntegralUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected limits, quotient real equality, host interval partitions, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint exposure, ordered subdivision exactness, dyadic mesh-bound stability, tag-window containment, RegSeqRat readback, Real seal nonescape, integration-consumer routing, transport, replay, provenance, and local naming for BEDC.Derived.BoundedRealIntervalPartitionUp.}
\end{closurestatus}
