\chapter{A Concrete Naming Certificate for $\SardTheoremFiniteJetUp$}
\label{ch:concrete-instances-sard-theorem-finite-jet-namecert}
\origin{human}

Following Sard and the finite-jet presentation of differential topology, the $\SardTheoremFiniteJetUp$ packet records the displayed local data by which a smooth map is inspected through finitely many derivative, chart, rank, and critical-value rows. It sits after the Frechet derivative surface of \autoref{ch:concrete-instances-frechet-derivative-namecert}, the local inverse-function route of \autoref{ch:concrete-instances-inverse-function-namecert}, the comparison discipline of \autoref{ch:concrete-instances-mean-value-theorem-namecert}, and the charted carrier of \autoref{ch:concrete-instances-manifold-namecert}. The packet names a finite jet certificate for critical-value exclusion windows; it is not the classical full measure-zero Sard theorem, not a transversality theorem, not a choice-selected regular-value principle, and not a standard bridge.

\begin{definition}[Sard theorem finite-jet carrier]
\label{def:sard-theorem-finite-jet-carrier}
A $\SardTheoremFiniteJetUp$ carrier is a finite $\BHist$ packet
$$
J=(M,F,D,R,V,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\ManifoldUp$ chart row naming the source and target chart windows in which the finite jet is read.
\item $F$ is the displayed map row, containing only the finite map observations inspected by the packet.
\item $D$ is the $\FrechetDerivativeUp$ jet row, recording the derivative orders and finite remainder windows consumed by the critical-value test.
\item $R$ is the rank-defect row, displaying which derivative minors are inspected and where the finite packet records criticality.
\item $V$ is the candidate value-window row, naming the finite output windows whose regular-value status is being tested.
\item $L$ is the local inverse or mean-value ledger supplied through $\InverseFunctionUp$ and $\MeanValueTheoremUp$ when a displayed noncritical branch is certified.
\item $H$ records componentwise $\hsame$ transport for the chart, map, derivative, rank, value-window, ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite value-window request through the chart, map, derivative, rank, and local ledger rows.
\item $P$ is the $\Pkg$ provenance over $\SardTheoremFiniteJetUp$, $\FrechetDerivativeUp$, $\InverseFunctionUp$, $\MeanValueTheoremUp$, $\ManifoldUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SardTheoremFiniteJetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for ambient measure zero, global transversality, choice-selected regular values, host smooth-function spaces, or a standard bridge.
\end{definition}

\begin{theorem}[Sard theorem finite-jet NameCert obligations]
\label{thm:sard-theorem-finite-jet-namecert-obligations}
For every accepted $\SardTheoremFiniteJetUp$ carrier $J=(M,F,D,R,V,L,H,C,P,N)$, the local $\NameCert_{\SardTheoremFiniteJetUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item charted carrier admission through $\ManifoldUp$ for the source and target windows;
\item finite derivative admission through $\FrechetDerivativeUp$ for the displayed jet orders and remainders;
\item rank-defect and value-window inspection through $R$ and $V$;
\item noncritical local handoff through $\InverseFunctionUp$ and $\MeanValueTheoremUp$ when the packet records a regular finite window;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$.
\end{enumerate}
Every accepted finite-jet regularity read factors through these five rows, and any disagreement between two accepted packets is visible in one of them.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:sard-theorem-finite-jet-carrier}. The rows $M,F,D,R,V,L,H,C,P,N$ are the whole accepted packet, so the chart, map, derivative, rank, value-window, and local ledger reads are finite $\BHist$ data.

The critical-value boundary is read only from $D,R,V$. The derivative row supplies the inspected jet windows, the rank-defect row records the displayed minors, and the value row records the finite output windows under consideration.

When a noncritical branch is exposed, the local ledger $L$ records the inverse-function and mean-value handoff. That handoff is local to the same chart and derivative rows, so it does not choose a global regular value or import a host transversality principle.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since no row stores ambient measure-zero data, global transversality, selected regular values, host smooth-function spaces, or bridge data, the five obligation rows exhaust the NameCert surface.
\end{proof}

\falsifiablePrediction{Every accepted $\SardTheoremFiniteJetUp$ packet must expose $\ManifoldUp$, $\FrechetDerivativeUp$, $\InverseFunctionUp$, $\MeanValueTheoremUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows before any finite-jet regularity read is public.}

\independenceWitness{frechet-derivative, inverse-function, mean-value-theorem, manifold: no listed sibling is bijective to $\SardTheoremFiniteJetUp$ because the Sard finite-jet packet jointly binds chart windows, map observations, derivative jets, rank-defect rows, value windows, local regularity ledger, transport, replay, provenance, and local naming in one carrier.}

\closureat{SardTheoremFiniteJetUp}{seedStr}

\begin{closurestatus}{\SardTheoremFiniteJetUp}
  \constructivestory{A $\SardTheoremFiniteJetUp$ packet is generated from Manifold chart rows, displayed map observations, Frechet derivative jet rows, rank-defect rows, finite value-window rows, an inverse-function and mean-value local ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sard-theorem-finite-jet-carrier} and \autoref{thm:sard-theorem-finite-jet-namecert-obligations} seed the finite Sard jet certificate over chart, derivative, rank, value-window, local regularity, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim the classical full measure-zero Sard theorem, transversality, choice-selected regular values, host smooth-function spaces, Lean verification, or standard bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite derivative admission, rank-defect inspection, value-window inspection, local inverse-function and mean-value handoff, and transport stability for BEDC.Derived.SardTheoremFiniteJetUp.}
\end{closurestatus}
