\chapter{A Concrete Naming Certificate for $\HausdorffDistanceUp$}
\label{ch:concrete-instances-hausdorff-distance-namecert}
\origin{human}

Following the Hausdorff--Kuratowski compact-set metric reading, the $\HausdorffDistanceUp$ packet records the scalar finite-distance certificate between two displayed nonempty compact subsets of one compact metric source. It sits next to the host hyperspace route of \autoref{ch:concrete-instances-hausdorff-metric-namecert}, consumes the compact-metric finite-net surface of \autoref{ch:concrete-instances-compactmetric-namecert}, and seals the resulting value through the real-name interface of \autoref{ch:concrete-instances-real-namecert}. The packet names the distance value as a finite BEDC carrier rather than treating $\HausdorffMetricUp$ itself as the only available consumer object.

\begin{definition}[Hausdorff distance finite carrier]
\label{def:hausdorff-distance-finite-carrier}
A $\HausdorffDistanceUp$ carrier is a finite $\BHist$ packet
$$
Q=(A,B,H,N_X,N_Y,D,E,R,T,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two nonempty compact-subset rows over the same compact metric source.
\item $H$ is the $\HausdorffMetricUp$ ledger row that records the finite directed comparisons already admitted by the neighbouring Hausdorff-metric certificate.
\item $N_X$ and $N_Y$ are finite net rows for the two compact-subset names, read from the $\CompactMetricUp$ and $\TotallyBoundedUp$ sources.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row controlling the displayed mesh, directed bound, and symmetric slack.
\item $E$ is the symmetric bound-exactness row, recording that the two directed finite-net estimates determine the same scalar tolerance window.
\item $R$ is the $\RealUp$ distance seal reached only after the ledger, nets, and dyadic tolerance rows have been displayed.
\item $T$ records componentwise $\hsame$ transport for $A,B,H,N_X,N_Y,D,E,R,C,P,L$.
\item $C$ records displayed $\Cont$ replay of the route from compact-subset rows through finite nets, symmetric bounds, and the real seal.
\item $P$ is the $\Pkg$ provenance over $\HausdorffDistanceUp$, $\HausdorffMetricUp$, $\CompactMetricUp$, $\TotallyBoundedUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\HausdorffDistanceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $A,B,H,N_X,N_Y,D,E,R,T,C,P,L$. It has no coordinate for a host hyperspace point, quotient subset equality, selected nearest point, open-cover compactness, or ambient supremum formation.
\end{definition}

\begin{theorem}[Hausdorff distance NameCert obligations]
\label{thm:hausdorff-distance-namecert-obligations}
For every accepted $\HausdorffDistanceUp$ carrier
$$
Q=(A,B,H,N_X,N_Y,D,E,R,T,C,P,L),
$$
the local $\NameCert_{\HausdorffDistanceUp}$ surface consists exactly of five finite obligation rows:
\begin{enumerate}
\item carrier admission for the two compact-subset rows, HausdorffMetric ledger, finite nets, dyadic tolerance row, symmetric bound row, Real seal, transport, replay, provenance, and local naming row;
\item symmetric bound exactness, requiring the directed finite-net estimates in $H$ and $E$ to share the dyadic tolerance budget recorded by $D$;
\item finite-net witness stability, requiring $N_X$ and $N_Y$ to remain attached to the same $\CompactMetricUp$ and $\TotallyBoundedUp$ sources under componentwise transport;
\item Real seal nonescape, requiring every scalar distance read to pass through $R$ after $H,N_X,N_Y,D,E$ have been displayed;
\item ledger nonescape, requiring $C,P,L$ to replay, source, and name only the displayed finite route and to export no host hyperspace point, quotient subset equality, selected nearest point, open-cover compactness, or ambient supremum row.
\end{enumerate}
No scalar Hausdorff distance obligation is stored outside these rows.
\end{theorem}

\begin{theorem}[Hausdorff distance scalar handoff]
\label{thm:hausdorff-distance-scalar-handoff}
Every Gromov--Hausdorff-facing, Vietoris-facing, or compact-subset consumer of an accepted $\HausdorffDistanceUp$ packet reads the scalar value only through the finite route
$$
A,B,H,N_X,N_Y,D,E \longmapsto R \longmapsto T,C,P,L .
$$
Thus the consumer receives a $\RealUp$ distance seal for the two displayed compact-subset rows without receiving a host hyperspace metric object, quotient subset equality, selected nearest point, open-cover compactness theorem, or ambient supremum principle.
\end{theorem}

\closureat{HausdorffDistanceUp}{seedStr}

\begin{closurestatus}{\HausdorffDistanceUp}
  \constructivestory{A $\HausdorffDistanceUp$ packet is generated from two nonempty compact-subset rows, a HausdorffMetricUp ledger, finite CompactMetricUp and TotallyBoundedUp net rows, a DyadicRatCore tolerance row, symmetric bound exactness, a RealUp distance seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-distance-finite-carrier}, \autoref{thm:hausdorff-distance-namecert-obligations}, and \autoref{thm:hausdorff-distance-scalar-handoff} seed the finite scalar Hausdorff distance certificate consumed by compact-metric downstream routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host hyperspaces, quotient subset equality, selected nearest points, open-cover compactness, ambient supremum formation, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, symmetric bound exactness, finite-net witness stability, RealUp seal nonescape, and ledger nonescape for BEDC.Derived.HausdorffDistanceUp.}
\end{closurestatus}
