\chapter{A Concrete Naming Certificate for $\RegularCauchyLocatedModulusUp$}
\label{ch:concrete-instances-regular-cauchy-located-modulus-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the
$\RegularCauchyLocatedModulusUp$ packet records the finite modulus evidence that
turns regular Cauchy rational windows into located real-name reads. It sits
between the dyadic arithmetic substrate of
\autoref{ch:concrete-instances-dyadicratcore-namecert}, the stream observation
surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular
rational sequence packet of
\autoref{ch:concrete-instances-regseqrat-namecert}, the located comparison rows
of \autoref{ch:concrete-instances-located-real-comparison-namecert}, and the
sealed real-name handoff of \autoref{ch:concrete-instances-real-namecert}.

\section{Located modulus carrier}
\label{sec:regular-cauchy-located-modulus-carrier}

\begin{definition}[Regular Cauchy located modulus carrier]
\label{def:regular-cauchy-located-modulus-carrier}
A $\RegularCauchyLocatedModulusUp$ carrier is a finite packet
$(D,S,Q,L,U,M,H,C,P,N)$ with the following displayed rows:
\begin{enumerate}
\item $D$, a $\DyadicRatCoreUp$ precision ledger whose positive rows name the
dyadic error budgets used by the modulus;
\item $S$, a $\StreamNameUp$ observation window for the rational name under
inspection;
\item $Q$, a $\RegSeqRatUp$ readback row exposing the regular Cauchy rational
values visible on $S$;
\item $L$ and $U$, lower and upper located comparison rows tied to the same
finite window and the same dyadic precision ledger;
\item $M$, a finite modulus row assigning to each displayed dyadic precision a
window depth after which the $Q$-values stay inside the $L,U$ located bracket;
\item $H$, the componentwise $\hsame$ transport rows for the dyadic ledger,
stream window, regular readback, located comparison rows, and modulus row;
\item $C$, the displayed $\Cont$ replay routes preserving the finite window and
modulus reads under transport;
\item $P$, the $\mathsf{Pkg}$ provenance rows for the dyadic ledger, stream
window, regular readback, located comparison evidence, and modulus ledger;
\item $N$, the local $\NameCert$ row binding these nine rows as one located
modulus certificate.
\end{enumerate}
The carrier contains no quotient equality of Cauchy names, no selected limit
point, no host real order predicate, and no ambient completeness principle.
\end{definition}

\begin{theorem}[Regular Cauchy located modulus NameCert obligations]
\label{thm:regular-cauchy-located-modulus-namecert-obligations}
The local $\NameCert_{\RegularCauchyLocatedModulusUp}$ surface for
\autoref{def:regular-cauchy-located-modulus-carrier} consists of six finite
obligations:
\begin{enumerate}
\item carrier admission: the rows $(D,S,Q,L,U,M,H,C,P,N)$ occur in the same
finite $\mathsf{BHist}$ packet;
\item window alignment: $S$ is the only observation window read by $Q$, by the
located comparison rows $L,U$, and by the modulus row $M$;
\item dyadic precision exactness: every modulus query in $M$ consumes a
positive $\DyadicRatCoreUp$ budget displayed in $D$;
\item regular readback confinement: all rational values inspected by $M$ come
through the $\RegSeqRatUp$ row $Q$ and not through an external sequence
selector;
\item located bracket handoff: the lower and upper comparison rows $L,U$ are
the only located evidence exported toward $\LocatedRealComparisonUp$;
\item transport stability: $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
move the dyadic ledger, window, readback, located brackets, and modulus row
componentwise.
\end{enumerate}
These obligations certify a finite located-modulus route for regular Cauchy
names. They do not certify quotient equality of names, chosen limits, total
order, or real completeness.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:regular-cauchy-located-modulus-carrier}. The projection exposes
the dyadic precision ledger $D$, the stream window $S$, the regular readback
$Q$, the located comparison rows $L,U$, and the modulus row $M$.

Window alignment and dyadic precision exactness are read directly from those
rows. Since $M$ has no coordinate except the displayed $D,S,Q,L,U$ data, each
precision query is evaluated against the same finite observation window and the
same regular Cauchy readback.

The located bracket handoff is componentwise. The $L,U$ rows are already the
displayed $\LocatedRealComparisonUp$ evidence, and the transport rows $H,C$
replay them together with $D,S,Q,M$.

Finally $P$ and $N$ record the provenance and local certificate for exactly
these rows. No extra coordinate can supply quotient stream equality, a selected
limit, a host real order predicate, or ambient completeness.
\end{proof}

\begin{theorem}[Regular Cauchy located modulus Real-seal handoff]
\label{thm:regular-cauchy-located-modulus-real-seal-handoff}
Every accepted $\RegularCauchyLocatedModulusUp$ packet exports toward
$\RealUp$ only the sealed read obtained from its $\RegSeqRatUp$ row $Q$, finite
$\StreamNameUp$ window $S$, positive $\DyadicRatCoreUp$ precision ledger $D$,
located comparison rows $L,U$, and modulus row $M$. The handoff preserves the
same $D,S,Q,L,U,M,H,C,P,N$ carrier rows and supplies no quotient equality of
Cauchy names, selected limit point, trichotomy, host real order predicate, or
ambient completeness principle.
\end{theorem}
\begin{proof}
Start with an accepted carrier and read the regular Cauchy name through $Q$ on
the displayed window $S$. The dyadic budgets used to test locatedness are the
positive rows of $D$, and the lower and upper comparison evidence is precisely
$L,U$.

The modulus row $M$ turns each displayed precision into a finite window-depth
claim over those same rows. Thus the Real-facing read has the data needed for a
sealed $\RealUp$ handoff without selecting a representative limit.

Transport is confined to $H$ and replayed by $C$. These rows preserve the
dyadic ledger, stream window, regular readback, located brackets, and modulus
ledger componentwise, while $P,N$ record provenance and local naming.

The carrier has no quotient, trichotomy, host order, selected limit, or
completeness coordinate. Hence the Real-seal consumer receives exactly the
finite located-modulus evidence stated above.
\end{proof}

\closureat{RegularCauchyLocatedModulusUp}{seedStr}

\begin{closurestatus}{\RegularCauchyLocatedModulusUp}
  \constructivestory{A $\RegularCauchyLocatedModulusUp$ packet is generated from a dyadic precision ledger, a StreamName observation window, a RegSeqRat readback, located comparison brackets, a finite modulus row, componentwise transport, replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-located-modulus-carrier}, \autoref{thm:regular-cauchy-located-modulus-namecert-obligations}, and \autoref{thm:regular-cauchy-located-modulus-real-seal-handoff} name the seed carrier, finite NameCert obligation surface, and Real-seal handoff for located moduli of regular Cauchy names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient equality of Cauchy names, selected limits, trichotomy, host real order, ambient completeness, or a standard bridge.}
  \upgradepath{To reach obligationClosure, the carrier, finite modulus obligations, and Real-seal handoff must be checked as BEDC packet obligations.}
\end{closurestatus}
