\chapter{A Concrete Naming Certificate for $\RegularCauchyCompletionUnitUp$}
\label{ch:concrete-instances-regular-cauchy-completion-unit-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion, the $\RegularCauchyCompletionUnitUp$ packet records the unit route from displayed regular Cauchy source data into the completion-facing seal. It sits between the regular-name source of \autoref{ch:concrete-instances-regularcauchyname-namecert}, the unit map of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the monadic completion surface of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, and the real completion boundary of \autoref{ch:concrete-instances-real-cauchy-completion-namecert}. Its finite reads pass through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ as exposed in \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names the source-to-completion unit as finite BEDC data; it is not quotient completion equality, a selected Cauchy representative, countable choice, or ambient completeness of $\RealUp$.

\begin{definition}[RegularCauchyCompletionUnit carrier]
\label{def:regular-cauchy-completion-unit-carrier}
A $\RegularCauchyCompletionUnitUp$ carrier is a finite $\BHist$ packet
$$
U=(G,R,S,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the source row, read either as a $\RegularCauchyNameUp$ packet or as the $\RegSeqRatUp$ regular rational Cauchy row already visible to a completion consumer.
\item $R$ is the unit-admission row stating that the displayed source row is admitted as the unit image before any completion-facing seal is consumed.
\item $S$ is the finite family of $\StreamNameUp$ windows through which the source row is inspected.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to those source windows and precision requests.
\item $E$ is the $\RealCauchyCompletionUp$ or $\RealUp$ seal handoff reached only after $G,R,S,D$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source, unit-admission row, stream windows, dyadic tolerance ledger, seal handoff, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from source inspection through unit admission, finite windows, tolerance readback, and seal handoff.
\item $P$ records $\Pkg$ provenance over $\RegularCauchyCompletionUnitUp$, $\RegularCauchyNameUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionMonadUp$, $\RealCauchyCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyCompletionUnitUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, a selected regular-Cauchy representative, countable-choice schedules, host sequence equality, an ambient completion theorem, or $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RegularCauchyCompletionUnit NameCert obligations]
\label{thm:regular-cauchy-completion-unit-namecert-obligations}
For an accepted $\RegularCauchyCompletionUnitUp$ carrier $U=(G,R,S,D,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyCompletionUnitUp}$ surface consists exactly of source admission through $G$, unit-route admission through $R$, finite $\StreamNameUp$ window exposure through $S$, $\DyadicRatCoreUp$ tolerance readback through $D$, $\RealCauchyCompletionUp$ or $\RealUp$ seal handoff through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-completion-unit-carrier}. Its displayed source row is $G$, and the unit-admission row is $R$.

The finite observation surface is $S,D$. The stream windows expose only scheduled source reads, and the dyadic ledger records only the tolerance data needed before completion-facing consumption.

The seal handoff $E$ is downstream of those rows. The structural rows $H,C,P,N$ transport, replay, source, and name the same route, so the local certificate is exhausted by the listed fields.
\end{proof}

\begin{theorem}[RegularCauchyCompletionUnit seal handoff]
\label{thm:regular-cauchy-completion-unit-seal-handoff}
Every $\RealCauchyCompletionUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionMonadUp$, or $\RealUp$ consumer of an accepted $\RegularCauchyCompletionUnitUp$ packet reaches the seal row $E$ only through the route
$$
G\longmapsto R\longmapsto S\longmapsto D\longmapsto E
$$
together with $H,C,P,N$. Thus the unit image is consumed as displayed regular Cauchy source data with finite windows and dyadic tolerance readback, not as a quotient class or selected completion representative.
\end{theorem}
\begin{proof}
Begin with a completion-facing consumer. By the carrier definition, the only source row available to the consumer is $G$, and the only unit-admission row is $R$.

The consumer must next pass through the finite windows $S$ and the dyadic tolerance ledger $D$. These rows are the displayed readback route inherited from the regular-name and regular-rational source surfaces.

Only after that route is available can $E$ be read. The rows $H,C,P,N$ attach transport, replay, provenance, and local naming to the same route, so the seal handoff is the displayed unit route and not a hidden completion object.
\end{proof}

\begin{theorem}[RegularCauchyCompletionUnit non-escape]
\label{thm:regular-cauchy-completion-unit-nonescape}
No accepted $\RegularCauchyCompletionUnitUp$ packet exports data outside $G,R,S,D,E,H,C,P,N$. In particular, it cannot be used to recover quotient completion equality, a selected regular-Cauchy representative, countable-choice schedules, host sequence equality, an ambient completion theorem, analytic closure of the monad, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Inspect the carrier. The source, unit-admission, window, tolerance, seal, transport, replay, provenance, and local-name rows are the only fields.

Apply \autoref{thm:regular-cauchy-completion-unit-namecert-obligations}. Every accepted obligation is a projection of those rows or a structural transport, replay, provenance, or naming row for them.

Finally use \autoref{thm:regular-cauchy-completion-unit-seal-handoff}. All completion-facing consumers pass through $G,R,S,D,E,H,C,P,N$, so no excluded quotient, choice, host, monadic closure, or completeness object can be exported.
\end{proof}

\begin{closurestatus}{\RegularCauchyCompletionUnitUp}
  \constructivestory{A $\RegularCauchyCompletionUnitUp$ packet is generated from a RegularCauchyName or RegSeqRat source row, unit admission, finite StreamName windows, a DyadicRatCore tolerance ledger, a RealCauchyCompletion or RealUp seal handoff, componentwise transport, displayed replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-completion-unit-carrier}, \autoref{thm:regular-cauchy-completion-unit-namecert-obligations}, \autoref{thm:regular-cauchy-completion-unit-seal-handoff}, and \autoref{thm:regular-cauchy-completion-unit-nonescape} seed the finite source-to-completion unit route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, quotient completion equality, selected representatives, countable choice, host sequence equality, monadic analytic closure, ambient completion, or $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, unit-route admission, finite window exposure, dyadic tolerance readback, seal handoff, transport stability, provenance, and non-escape for the displayed packet.}
\end{closurestatus}
