\chapter{A Concrete Naming Certificate for $\FrechetUrysohnUp$}
\label{ch:concrete-instances-frechet-urysohn-namecert}
\origin{human}

Following Frechet and Urysohn's sequential analysis of closure in topology, the $\FrechetUrysohnUp$ packet records the finite data by which a point is certified as sequentially reachable from a displayed subset rather than assuming an ambient topological closure operator. It sits between the finite real-valued sequence surface of \autoref{ch:concrete-instances-real-sequence-space-namecert}, the sequential compactness packet of \autoref{ch:concrete-instances-sequentialcompact-namecert}, and the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}.

\begin{definition}[Frechet-Urysohn carrier]
\label{def:frechet-urysohn-carrier}
A $\FrechetUrysohnUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,S,W,R,A,X,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the topology carrier row, containing the named point, the displayed subset, and the finite neighborhood probes used by the closure read.
\item $S$ is the sequence-space row over $\RealSequenceSpaceUp$, recording the accepted real-valued or chart-valued sequence route used to approach the named point.
\item $W$ is the $\StreamNameUp$ window schedule for the finite initial segments and tail windows visible to the classifier.
\item $R$ is the $\RealUp$ seal row attached to the coordinate reads that witness convergence through $S$ and $W$.
\item $A$ is the closure-witness row, displaying that every inspected tail window lies in the named subset and that the limit read is the named point.
\item $X$ is the transport row for the topology probes, sequence-space rows, StreamName windows, Real seal, closure witness, replay, provenance, and local naming data.
\item $H$ records componentwise $\hsame$ transport along the same displayed rows.
\item $C$ records displayed $\Cont$ replay from a closure request through $T,S,W,R,A,X$.
\item $P$ is the $\Pkg$ provenance over $\FrechetUrysohnUp$, $\RealSequenceSpaceUp$, $\SequentialCompactUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FrechetUrysohnUp}$ row.
\end{enumerate}
The classifier has no coordinate for arbitrary nets, choice-selected sequences, host closure equality, excluded middle over neighborhoods, or an ambient compactness theorem.
\end{definition}

\begin{theorem}[Frechet-Urysohn NameCert obligations]
\label{thm:frechet-urysohn-namecert-obligations}
For every accepted $\FrechetUrysohnUp$ carrier $Q=(T,S,W,R,A,X,H,C,P,N)$, the local $\NameCert_{\FrechetUrysohnUp}$ surface consists exactly of finite $\BHist$ rows for topology admission, sequence-space admission, StreamName windowing, Real-seal ordering, closure-witness display, transport, replay, provenance, and local naming. Every sequential-closure classifier read must pass through $T,S,W,R,A,X,H,C,P,N$ in that order, and any disagreement between two accepted packets must be visible in one of those displayed rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:frechet-urysohn-carrier}. The packet exposes the topology row, the real sequence-space row, the finite StreamName windows, the Real seal, and the closure-witness row before any structural replay is available.

The NameCert obligations are therefore row-local. Topology admission is read from $T$, the sequence route from $S$, the finite windows from $W$, the coordinate seal from $R$, and the sequential closure witness from $A$.

The structural rows $X,H,C,P,N$ then transport, compare, replay, source, and name the same finite packet. Since the carrier contains none of the excluded host-side coordinates, a classifier disagreement cannot be hidden outside the displayed rows.
\end{proof}

\begin{theorem}[Frechet-Urysohn sequential closure handoff]
\label{thm:frechet-urysohn-sequential-closure-handoff}
Every consumer that reads a point as belonging to the sequential closure of a displayed subset through an accepted $\FrechetUrysohnUp$ carrier factors through
$$
\RealSequenceSpaceUp,\qquad
\SequentialCompactUp,\qquad
\StreamNameUp,\qquad
\RealUp
$$
and then through the closure-witness row $A$. The handoff exports only the finite sequence windows, the accepted sequence-space route, the Real seal, and the displayed tail-in-subset witness; it does not export arbitrary nets, countable choice, host closure equality, or ambient topological compactness.
\end{theorem}
\begin{proof}
Start with an accepted sequential-closure read. By \autoref{thm:frechet-urysohn-namecert-obligations}, the read first enters the topology row $T$ and then the sequence-space row $S$ with its displayed StreamName window schedule $W$.

The Real seal $R$ and the closure-witness row $A$ are downstream of the same sequence route. The witness can therefore certify only the inspected tail windows and the displayed limit read named by the packet.

The sequential compactness reference is consumed as a finite comparison boundary rather than as an ambient compactness theorem. The structural rows $X,H,C,P,N$ preserve this same route, so the consumer receives a sequential handoff but no hidden net, selected sequence, host equality, or external closure principle.
\end{proof}

\closureat{FrechetUrysohnUp}{seedStr}

\begin{closurestatus}{\FrechetUrysohnUp}
  \constructivestory{A $\FrechetUrysohnUp$ packet is generated from a topology carrier row, a real sequence-space row, StreamName windows, a Real seal, a closure-witness row, transport, componentwise hsame rows, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:frechet-urysohn-carrier}, \autoref{thm:frechet-urysohn-namecert-obligations}, and \autoref{thm:frechet-urysohn-sequential-closure-handoff} seed the sequential-closure carrier over finite topology, sequence-space, window, Real, and witness rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary nets, countable choice, host closure equality, excluded middle over neighborhoods, ambient compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, sequence-space admission, finite-window ordering, Real-seal ordering, closure-witness display, and transport stability for the same packet.}
\end{closurestatus}
