\chapter{A Concrete Naming Certificate for $\HyperbolicBoundaryPhaseAuditUp$}
\label{ch:concrete-instances-hyperbolic-boundary-phase-audit-namecert}
\origin{ai}

The $\HyperbolicBoundaryPhaseAuditUp$ packet realizes the boundary-phase audit face of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits after the observer-expansion ledger of \autoref{ch:concrete-instances-hyperbolic-expansion-ledger-namecert}, the boundary-geodesic route of \autoref{ch:concrete-instances-hyperbolic-geodesic-boundary-namecert}, the horocycle packet of \autoref{ch:concrete-instances-hyperbolic-horocycle-namecert}, the phase-ledger horocycle packet of \autoref{ch:concrete-instances-phase-ledger-horocycle-namecert}, and the boundary-fixed disk transport route of \autoref{ch:concrete-instances-poincare-boundary-fixed-transport-namecert}. The packet names an audit row for checking that a visible boundary-phase read has passed through the displayed hyperbolic ledger, boundary, horocycle, and transport surfaces; it is not a second horocycle carrier, not a host ideal-boundary quotient, and not a physical observer trajectory.

\falsifiablePrediction{Every accepted $\HyperbolicBoundaryPhaseAuditUp$ read factors through displayed $\HyperbolicExpansionLedgerUp$, $\HyperbolicGeodesicBoundaryUp$, $\HyperbolicHorocycleUp$, $\PhaseLedgerHorocycleUp$, $\PoincareBoundaryFixedTransportUp$, transport, replay, provenance, and local $\NameCert$ rows before it exports a boundary-phase audit verdict.}

\independenceWitness{hyperbolic-expansion-ledger, hyperbolic-geodesic-boundary, hyperbolic-horocycle, phase-ledger-horocycle, poincare-boundary-fixed-transport: the expansion ledger records records-side growth without a boundary-phase audit verdict; the geodesic-boundary packet records far-end incidence without horocycle phase accounting; the horocycle packet records boundary tangency without focused phase-ledger provenance; the phase-ledger horocycle packet records the boundary-transport route without a separate audit verdict; and the boundary-fixed transport packet records preserved disk transport without ledger-phase coverage. None is bijective to $\HyperbolicBoundaryPhaseAuditUp$.}

\begin{definition}[Hyperbolic boundary-phase audit carrier]
\label{def:hyperbolic-boundary-phase-audit-carrier}
A $\HyperbolicBoundaryPhaseAuditUp$ carrier is a finite $\BHist$ packet
$$
A=(X,G,Q,L,T,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\HyperbolicExpansionLedgerUp$ observer-expansion ledger row.
\item $G$ is the $\HyperbolicGeodesicBoundaryUp$ boundary-geodesic incidence row.
\item $Q$ is the $\HyperbolicHorocycleUp$ boundary-tangent row.
\item $L$ is the $\PhaseLedgerHorocycleUp$ focused phase-ledger route.
\item $T$ is the $\PoincareBoundaryFixedTransportUp$ boundary-preserving disk-transport row.
\item $V$ is the audit verdict row, recording that the visible boundary-phase read has consumed $X,G,Q,L,T$ before any public verdict is exported.
\item $H$ records componentwise $\hsame$ transport for the expansion ledger, boundary-geodesic, horocycle, phase-ledger, transport, audit, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through the same ordered audit route.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicBoundaryPhaseAuditUp$, $\HyperbolicExpansionLedgerUp$, $\HyperbolicGeodesicBoundaryUp$, $\HyperbolicHorocycleUp$, $\PhaseLedgerHorocycleUp$, $\PoincareBoundaryFixedTransportUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicBoundaryPhaseAuditUp}$ row.
\end{enumerate}
The carrier exports no host hyperbolic plane, quotient ideal-boundary equality, selected boundary representative, global clock, physical observer path, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Hyperbolic boundary-phase audit NameCert obligations]
\label{thm:hyperbolic-boundary-phase-audit-namecert-obligations}
For every accepted $\HyperbolicBoundaryPhaseAuditUp$ carrier $A=(X,G,Q,L,T,V,H,C,P,N)$, the local $\NameCert_{\HyperbolicBoundaryPhaseAuditUp}$ surface consists exactly of observer-expansion ledger admission, boundary-geodesic incidence, horocycle boundary tangency, focused phase-ledger route admission, boundary-fixed transport, audit verdict exposure, componentwise transport, displayed continuation replay, package provenance, and local naming.
\end{theorem}
\begin{proof}
Project the accepted carrier. The analytic route begins with the expansion ledger $X$, then reads the boundary-geodesic row $G$, the horocycle row $Q$, the phase-ledger horocycle row $L$, and the boundary-fixed transport row $T$.

The audit verdict $V$ is downstream of those five rows. It therefore cannot certify a boundary-phase read unless the expansion, boundary, horocycle, phase-ledger, and transport surfaces have already been displayed.

The structural rows $H,C,P,N$ preserve and name that route. Since the carrier has no coordinate for a host hyperbolic plane, quotient boundary equality, selected boundary representative, global clock, physical observer path, Lean verification, or bridge checking, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Hyperbolic boundary-phase audit route nonescape]
\label{thm:hyperbolic-boundary-phase-audit-route-nonescape}
Every boundary-phase audit verdict exported by an accepted $\HyperbolicBoundaryPhaseAuditUp$ packet factors through
$$
\HyperbolicExpansionLedgerUp \longmapsto \HyperbolicGeodesicBoundaryUp \longmapsto \HyperbolicHorocycleUp \longmapsto \PhaseLedgerHorocycleUp \longmapsto \PoincareBoundaryFixedTransportUp
$$
before the audit verdict row is visible. The verdict exports only the finite audit route carried by $A=(X,G,Q,L,T,V,H,C,P,N)$, not a host ideal-boundary quotient, a selected boundary representative, a physical observer trajectory, a global clock, or a completed hyperbolic surface.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:hyperbolic-boundary-phase-audit-namecert-obligations}. They place the expansion ledger, boundary-geodesic row, horocycle row, phase-ledger horocycle route, and boundary-fixed transport before the audit verdict.

Read the sibling packets in order. \autoref{thm:hyperbolic-expansion-ledger-cont-growth-route} supplies the records-side expansion route, \autoref{thm:hyperbolic-geodesic-boundary-phase-handoff} supplies the boundary-geodesic handoff, \autoref{thm:hyperbolic-horocycle-namecert-obligations} supplies the horocycle boundary-tangency route, and \autoref{thm:phase-ledger-horocycle-namecert-obligations} supplies the focused phase-ledger route.

Finally consume the boundary-fixed transport row and the structural rows $H,C,P,N$. Because no other carrier coordinate exists, the audit verdict cannot escape to host boundary equality, selected representatives, physical observer motion, global clocks, or completed hyperbolic geometry.
\end{proof}

The Lean follow-up for this packet must provide explicit $\mathsf{Nontrivial}\ \HyperbolicBoundaryPhaseAuditUp$ and $\mathsf{FieldFaithful}\ \HyperbolicBoundaryPhaseAuditUp$ TasteGate instances. Those instances must keep $X,G,Q,L,T,V,H,C,P,N$ as separate fields before any checked carrier-alignment theorem can serve as a public TasteGate realization.

\closureat{HyperbolicBoundaryPhaseAuditUp}{seedStr}

\begin{closurestatus}{\HyperbolicBoundaryPhaseAuditUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-boundary-phase-audit-carrier}, \autoref{thm:hyperbolic-boundary-phase-audit-namecert-obligations}, and \autoref{thm:hyperbolic-boundary-phase-audit-route-nonescape} seed the finite boundary-phase audit route over expansion-ledger, boundary-geodesic, horocycle, phase-ledger, boundary-fixed transport, audit, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host hyperbolic geometry, quotient ideal-boundary equality, selected boundary representatives, physical observer trajectories, global clocks, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, expansion-ledger routing, boundary-geodesic handoff, horocycle incidence, phase-ledger coverage, boundary-fixed transport, audit verdict exactness, TasteGate nontriviality, FieldFaithful coverage, and local naming for BEDC.Derived.HyperbolicBoundaryPhaseAuditUp.}
  \constructivestory{A $\HyperbolicBoundaryPhaseAuditUp$ packet is generated from a HyperbolicExpansionLedger row, HyperbolicGeodesicBoundary row, HyperbolicHorocycle row, PhaseLedgerHorocycle route, PoincareBoundaryFixedTransport row, audit verdict row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
