\chapter{A Concrete Naming Certificate for $\CauchyCompletionStableReflectionUp$}
\label{ch:concrete-instances-cauchy-completion-stable-reflection-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion, the $\CauchyCompletionStableReflectionUp$ packet records the stable reflection surface by which a displayed completion functor, its universal property, separatedness, regular rational sequence data, and terminal real-name rows remain attached to one finite NameCert route. It sits after the completion functor of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, the universal handoff of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the separated limit classifier of \autoref{ch:concrete-instances-separatedmetric-namecert}, the regular rational sequence rows of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a stable reflection certificate for the displayed route; it does not assert quotient completion construction, selected limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy completion stable reflection carrier]
\label{def:cauchy-completion-stable-reflection-carrier}
A $\CauchyCompletionStableReflectionUp$ carrier is a finite $\BHist$ packet
$$
R=(F,U,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyCompletionFunctorUp$ row, containing the named source metric, target completion surface, and functorial map route.
\item $U$ is the $\CompletionUniversalPropertyUp$ row, storing the extension and uniqueness handoff for maps out of the displayed dense source.
\item $S$ is the $\SeparatedMetricUp$ row, recording the zero-distance classifier used for completion-limit uniqueness.
\item $Q$ is the $\RegSeqRatUp$ row, carrying the regular rational sequence schedules and finite tolerance windows read by the completion route.
\item $E$ is the $\RealUp$ seal row reached from the regular sequence and zero-distance data.
\item $H$ records componentwise $\hsame$ transport for functor, universal-property, separatedness, regular-sequence, Real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from $F,Q$ through $U,S,E$ and back to the local naming row.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionStableReflectionUp$, $\CauchyCompletionFunctorUp$, $\CompletionUniversalPropertyUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionStableReflectionUp}$ row.
\end{enumerate}
The carrier contains no quotient completion object, no chosen representative of a limit, no external completeness theorem for $\RealUp$, and no route outside the displayed BEDC rows.
\end{definition}

\begin{theorem}[Cauchy completion stable reflection NameCert obligations]
\label{thm:cauchy-completion-stable-reflection-namecert-obligations}
For every accepted $\CauchyCompletionStableReflectionUp$ carrier $R=(F,U,S,Q,E,H,C,P,N)$, the local $\NameCert_{\CauchyCompletionStableReflectionUp}$ surface consists exactly of carrier admission for $F,U,S,Q,E,H,C,P,N$; functor stability through $F$; extension uniqueness through $U$; separated zero-distance classification through $S$; regular rational window control through $Q$; Real seal confinement through $E$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $C$; provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-stable-reflection-carrier}. The accepted packet displays exactly the completion functor row, the universal-property row, the separatedness row, the regular rational sequence row, the Real seal, and the structural rows.

Functor stability and extension uniqueness are read in that order. The row $F$ supplies the completion-facing map route, while $U$ allows an extension consumer to compare two displayed routes only after they share the same source, completion surface, and regular sequence data.

Separatedness and Real sealing are likewise internal to the packet. The row $S$ turns zero-distance evidence into classifier equivalence, the row $Q$ supplies the finite regular rational windows that feed the completion comparison, and $E$ seals the resulting value inside the displayed $\RealUp$ boundary.

Transport, replay, provenance, and local naming are exhausted by $H,C,P,N$. Since the carrier has no quotient object, selected limit, countable-choice schedule, trichotomy row, or ambient Real-completeness coordinate, every local NameCert obligation is confined to the listed rows.
\end{proof}

\begin{theorem}[Cauchy completion stable reflection extension route]
\label{thm:cauchy-completion-stable-reflection-extension-route}
Every extension-facing consumer of an accepted $\CauchyCompletionStableReflectionUp$ carrier factors through the finite route
$$
\CauchyCompletionFunctorUp \longmapsto \CompletionUniversalPropertyUp \longmapsto \SeparatedMetricUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Equivalently, the consumer receives the rows $F,U,S,Q,E,H,C,P,N$ and no quotient completion carrier, selected representative, hidden completion theorem, countable-choice schedule, trichotomy row, or off-packet certificate.
\end{theorem}
\begin{proof}
Begin with the functor row $F$. It is the only coordinate that exposes the completion-facing map route and the source-to-completion handoff.

Next use the universal-property row $U$. It compares extension candidates only after the route through $F$ is fixed, so extension uniqueness cannot be read as a host equality or as a selected representative of a completed object.

The separatedness and regular-sequence rows then bind the uniqueness read to finite BEDC data. The row $S$ supplies the zero-distance classifier, $Q$ supplies the regular rational windows that make the completion comparison visible, and $E$ confines the resulting value to the Real seal.

Finally $H,C,P,N$ transport, replay, source, and name that same route. Coordinate exhaustion rules out any hidden quotient completion, ambient Real-completeness theorem, choice schedule, trichotomy row, or off-packet certificate.
\end{proof}
