\chapter{A Concrete Naming Certificate for $\UniformCompletionUniversalPropertyUp$}
\label{ch:concrete-instances-uniform-completion-universal-property-namecert}
\origin{human}

Following Bishop and Bridges constructive completion and Kelley uniform-space terminology, the $\UniformCompletionUniversalPropertyUp$ packet records the uniform analogue of the L10 completion universal property. It sits after the uniform-completion carrier of \autoref{ch:concrete-instances-uniformcompletion-namecert}, the generic completion surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, and the regular-rational readbacks of \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names extension and uniqueness only through finite uniform rows, not through quotient completions, selected limits, ambient complete spaces, or choice.

\begin{definition}[Uniform completion universal-property carrier]
\label{def:uniform-completion-universal-property-carrier}
A $\UniformCompletionUniversalPropertyUp$ carrier is a finite $\BHist$ packet
$$
K=(U,D,T,E,L,M,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the uniform source row, exposing only the displayed $\UniformSpaceUp$ entourages and their finite source windows.
\item $D$ is the dense unit row from the source into the completion carrier, aligned with the $\UniformCompletionUp$ unit surface.
\item $T$ is the uniformly continuous target row, naming the complete separated target interface through finite entourage/modulus data.
\item $E$ is the extension row for uniformly continuous source consumers, read only after $U,D,T$ have been displayed.
\item $L$ is the uniqueness row, comparing two displayed extensions by $\hsame$ over the dense unit and the same target row.
\item $M$ is the entourage/modulus ledger for source entourages, target entourages, and the finite modulus witnesses used by $E$ and $L$.
\item $W$ is the readback row for $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ observations downstream of the same uniform route.
\item $H$ stores componentwise $\hsame$ transport for the source, dense unit, target, extension, uniqueness, modulus, readback, continuation, provenance, and naming rows.
\item $C$ stores displayed $\Cont$ replay from source windows through the dense unit, target modulus, extension row, uniqueness row, and readback row.
\item $P$ is the $\Pkg$ provenance over $\UniformCompletionUniversalPropertyUp$, $\UniformCompletionUp$, $\CompletionUniversalPropertyUp$, $\UniformSpaceUp$, $\UniformModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformCompletionUniversalPropertyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $U,D,T,E,L,M,W,H,C,P,N$. It has no coordinate for quotient completion points, selected representatives, ambient target completeness, host function extensionality, or countable choice.
\end{definition}

\begin{theorem}[Uniform completion universal-property NameCert obligations]
\label{thm:uniform-completion-universal-property-namecert-obligations}
For every accepted $\UniformCompletionUniversalPropertyUp$ carrier $K=(U,D,T,E,L,M,W,H,C,P,N)$, the local $\NameCert_{\UniformCompletionUniversalPropertyUp}$ surface consists exactly of carrier admission for the eleven displayed rows, uniform-source exposure through $U$, dense-unit exposure through $D$, complete separated target exposure through $T$, extension existence through $E$, uniqueness through $L$, entourage/modulus accounting through $M$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ readbacks through $W$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:uniform-completion-universal-property-carrier}. The source, dense unit, target, extension, uniqueness, modulus ledger, readback row, transport, replay, provenance, and local name are exactly the displayed coordinates of one finite $\BHist$ packet.

The extension row $E$ is available only after the source row $U$, dense unit row $D$, target row $T$, and entourage/modulus ledger $M$ have been displayed. The uniqueness row $L$ compares extensions over the same rows by the recorded $\hsame$ ledger.

The readback row $W$ is downstream of that uniform route. Since the classifier has no remaining coordinate for selected limits, quotient completions, host function equality, countable choice, or ambient target completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Uniform completion universal-property extension uniqueness]
\label{thm:uniform-completion-universal-property-extension-uniqueness}
Let $K=(U,D,T,E,L,M,W,H,C,P,N)$ be an accepted $\UniformCompletionUniversalPropertyUp$ carrier. Every extension-and-uniqueness consumer factors through
$$
U,D,T,M\longmapsto E\longmapsto L\longmapsto W
$$
together with $H,C,P,N$. Thus extension existence, uniqueness over the dense unit, and any $\StreamNameUp$, $\RegSeqRatUp$, or $\RealUp$ readback are all read from the same finite uniform packet, and no consumer obtains a quotient completion, selected extension, ambient complete target theorem, or choice principle.
\end{theorem}
\begin{proof}
Read the carrier definition. The extension coordinate is $E$, and its stated inputs are the uniform source $U$, dense unit $D$, uniformly continuous target $T$, and entourage/modulus ledger $M$.

The uniqueness row $L$ is not an independent equality principle. It compares displayed extensions only along the same dense unit and target row, using the componentwise $\hsame$ route recorded by $H$ and replayed by $C$.

Finally inspect the downstream rows. The readback coordinate $W$ is attached to the same route, while $P$ and $N$ record provenance and local naming. Row exhaustion excludes every omitted host object, so the extension-and-uniqueness surface is exactly the finite route displayed above.
\end{proof}

\falsifiablePrediction{Every accepted $\UniformCompletionUniversalPropertyUp$ consumer that exports extension existence or uniqueness while omitting the uniform source, dense unit, uniformly continuous target, extension row, uniqueness row, entourage/modulus ledger, readback row, transport, replay, provenance, or local naming row refutes the packet.}

\independenceWitness{uniformcompletion, completionuniversalproperty, uniformspace, uniformmodulus, streamname, regseqrat, real: $\UniformCompletionUniversalPropertyUp$ is not bijective to any listed sibling because it jointly carries uniform source, dense unit, target continuity, extension, uniqueness, modulus ledger, readbacks, transport, replay, provenance, and local NameCert rows in one universal-property packet.}

\closureat{UniformCompletionUniversalPropertyUp}{seedStr}

\begin{closurestatus}{\UniformCompletionUniversalPropertyUp}
  \constructivestory{A $\UniformCompletionUniversalPropertyUp$ packet is generated from a uniform source row, dense unit row, uniformly continuous target row, extension row, uniqueness row, entourage/modulus ledger, StreamName/RegSeqRat/Real readbacks, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-completion-universal-property-carrier}, \autoref{thm:uniform-completion-universal-property-namecert-obligations}, and \autoref{thm:uniform-completion-universal-property-extension-uniqueness} seed the finite uniform universal-property certificate surface.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.UniformCompletionUniversalPropertyUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected extensions, ambient complete target theorems, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, extension existence, uniqueness, readback nonescape, transport replay, provenance, and TasteGate field faithfulness for BEDC.Derived.UniformCompletionUniversalPropertyUp.}
\end{closurestatus}
