\chapter{A Concrete Naming Certificate for $\WhitneyExtensionFiniteJetUp$}
\label{ch:concrete-instances-whitney-extension-finite-jet-namecert}
\origin{human}

Following Whitney's finite-jet extension theorem and the constructive finite-row presentation of differentiability data, the $\WhitneyExtensionFiniteJetUp$ packet records a finite jet family over a closed carrier together with the compatibility estimates needed by extension consumers. It sits over the real and order-facing rows of \autoref{ch:concrete-instances-real-namecert} and \autoref{ch:concrete-instances-real-alg-order-namecert}, the metric and ball rows of \autoref{ch:concrete-instances-metric-namecert} and \autoref{ch:concrete-instances-metricball-namecert}, the derivative-facing surface of \autoref{ch:concrete-instances-derivative-namecert}, and the Sobolev trace boundary of \autoref{ch:concrete-instances-sobolev-trace-namecert}. The packet is a finite NameCert carrier for jet compatibility and consumer routing; it is not a global smooth extension operator, a selected extension function, host compactness, choice, or ambient $\RealUp$ completeness.

\begin{definition}[Whitney finite-jet extension carrier]
\label{def:whitney-extension-finite-jet-carrier}
A $\WhitneyExtensionFiniteJetUp$ carrier is a finite $\BHist$ packet
$$
W=(X,F,J,A,E,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricUp$ or Euclidean metric carrier whose distance rows supply the only spatial comparisons used by the packet.
\item $F$ is the closed-set classifier row naming the finite observation domain on which jets are read.
\item $J$ is the finite jet table, containing the displayed value and derivative rows indexed by the admitted multiindex budget.
\item $A$ is the $\RealAlgOrderUp$ comparison ledger for the Whitney difference quotients, radius bounds, and finite error budgets.
\item $E$ is the local extension-admissibility ledger, recording that every requested jet comparison is routed through $F,J,A$ and the displayed metric-ball scales.
\item $R$ is the readback row for derivative-facing and Sobolev-trace-facing consumers.
\item $H$ records componentwise $\hsame$ transport for the carrier, closed-set classifier, jet table, order ledger, extension-admissibility ledger, readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite jet request through $X,F,J,A,E,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\WhitneyExtensionFiniteJetUp$, $\MetricUp$, $\MetricBallUp$, $\RealUp$, $\RealAlgOrderUp$, $\DerivativeUp$, $\SobolevTraceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\WhitneyExtensionFiniteJetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,F,J,A,E,R,H,C,P,N$. It has no coordinate for a host smooth function, a selected extension, compactness, arbitrary choice, quotient equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Whitney finite-jet NameCert obligations]
\label{thm:whitney-extension-finite-jet-namecert-obligations}
For every accepted $\WhitneyExtensionFiniteJetUp$ carrier $W=(X,F,J,A,E,R,H,C,P,N)$, the local $\NameCert_{\WhitneyExtensionFiniteJetUp}$ surface consists exactly of the finite rows named in \autoref{def:whitney-extension-finite-jet-carrier}: carrier admission for $X,F,J,A,E,R,H,C,P,N$, closed-set classifier stability, finite jet-table stability, order-ledger comparison for the Whitney estimates, extension-admissibility replay through metric-ball scales, derivative and Sobolev trace readback, transport, provenance, and local naming. No obligation row stores a host extension function, a global smoothness theorem, a selected representative, compactness, choice, quotient equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:whitney-extension-finite-jet-carrier}. The only geometric data are $X$ and $F$, and the only analytic data are the finite jet table $J$, the comparison ledger $A$, the extension-admissibility row $E$, and the readback row $R$.

The NameCert obligations are therefore rowwise. A finite jet request first names the metric carrier and closed-set classifier, then opens the jet table and the order-facing comparison ledger before any admissibility claim is available.

The admissibility row $E$ is the only coordinate that relates two jet reads at a displayed scale. It forces every difference-quotient and remainder comparison through $F,J,A$ and the relevant metric-ball radius rather than through a host extension function.

Finally, $H,C,P,N$ transport, replay, package, and name exactly the same route. Since the carrier contains no coordinate for a selected smooth extension, compactness, arbitrary choice, quotient equality, trichotomy, or ambient Real completeness, none of those objects can become a local obligation.
\end{proof}

\begin{theorem}[Whitney finite-jet consumer boundary]
\label{thm:whitney-extension-finite-jet-consumer-boundary}
Every $\DerivativeUp$, $\SobolevTraceUp$, $\MetricBallUp$, or $\RealAlgOrderUp$ consumer reading an accepted $\WhitneyExtensionFiniteJetUp$ carrier must factor through the displayed route
$$
X,F \longmapsto J,A \longmapsto E,R \longmapsto H,C,P,N .
$$
The consumer receives finite jet compatibility, order-facing estimates, and derivative or trace readback only along this route. It receives no global extension operator, no selected smooth function, no host compactness theorem, no arbitrary choice principle, no quotient equality, no trichotomy, and no ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a consumer read. By \autoref{def:whitney-extension-finite-jet-carrier}, the read can inspect only the metric carrier $X$, the closed-set classifier $F$, the jet table $J$, the comparison ledger $A$, and the admissibility row $E$ before it reaches derivative-facing or trace-facing output.

The row $R$ supplies the public readback boundary. It exposes the finite derivative and trace-facing records already justified by $E$, but it does not introduce a host smooth function or select an extension outside the displayed rows.

The structural rows preserve the same route. Componentwise transport and continuation replay move the packet through $H$ and $C$, while $P$ and $N$ record provenance and local naming. Thus every downstream consumer remains inside the finite Whitney jet surface.
\end{proof}

\closureat{WhitneyExtensionFiniteJetUp}{seedStr}

\begin{closurestatus}{\WhitneyExtensionFiniteJetUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:whitney-extension-finite-jet-carrier}, \autoref{thm:whitney-extension-finite-jet-namecert-obligations}, and \autoref{thm:whitney-extension-finite-jet-consumer-boundary} seed the finite Whitney jet packet over metric carriers, closed-set classifier rows, jet tables, order-facing estimates, and derivative or Sobolev trace readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close the classical global Whitney theorem, a selected smooth extension operator, compactness, arbitrary choice, quotient equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, jet-table stability, order-ledger comparison, extension-admissibility replay, derivative or trace readback, transport, provenance, and local naming for BEDC.Derived.WhitneyExtensionFiniteJetUp.}
  \constructivestory{A $\WhitneyExtensionFiniteJetUp$ packet is generated from a MetricUp carrier, a closed-set classifier row, a finite jet table, a RealAlgOrderUp comparison ledger, a local extension-admissibility row, derivative or Sobolev trace readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
