\chapter{A Concrete Naming Certificate for $\RadialWobbleSpectrumUp$}
\label{ch:concrete-instances-radial-wobble-spectrum-namecert}
\origin{ai}

The $\RadialWobbleSpectrumUp$ packet realizes the radial spectral surface of \autoref{thm:philosophy-radial-wobble-spectrum} as finite BEDC NameCert data. It consumes the boundary-tile coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the support-closure algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}, the hyperbolic metric reading of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, and the substrate trace invariant of \autoref{ch:concrete-instances-substrate-trace-invariant-namecert}. The packet names radial-shell, spectral-hinge, wobble-edge, and trigger-ledger rows; it is not a biological code table, stochastic evolutionary model, quotient codon semantics, or hidden spectral oracle.

\begin{definition}[Radial wobble spectrum carrier]
\label{def:radial-wobble-spectrum-carrier}
A $\RadialWobbleSpectrumUp$ carrier is a finite $\BHist$ packet
$$
R=(T,S,H,W,L,M,A,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\SixBoundaryTileCoverageUp$ boundary-tile coverage row, exposing the finite trigger support read by the radial packet.
\item $S$ is the radial-shell row, recording the six displayed states $X_{3},X_{2},X_{1},X_{0},Y_{R},Y_{Y}$ and their finite adjacency counts.
\item $H$ is the spectral-hinge row, recording the cubic hinge $r^{3}-12r^{2}+26r-9$ and the Perron read attached to the radial matrix.
\item $W$ is the wobble-edge row, recording the $f_{3}$ self-loop contribution and its normalized contribution to the killed bit-flip spectrum.
\item $L$ is the $\WindowCoverageTriggerAlgebraUp$ trigger ledger, binding support closure, residue accounting, blocker rows, and coverage thresholds to the same radial read.
\item $M$ is the $\HyperbolicMetricUp$ metric-read row used only as a boundary geometry witness for the radial shells.
\item $A$ is the $\SubstrateTraceInvariantUp$ substrate trace row, preserving the source trace across shell, hinge, wobble, and trigger reads.
\item $Q$ records componentwise $\hsame$ transport and displayed $\Cont$ replay for $T,S,H,W,L,M,A$.
\item $P$ records $\Pkg$ provenance over $\RadialWobbleSpectrumUp$, $\SixBoundaryTileCoverageUp$, $\WindowCoverageTriggerAlgebraUp$, $\HyperbolicMetricUp$, $\SubstrateTraceInvariantUp$, the source vision of \autoref{thm:philosophy-radial-wobble-spectrum}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RadialWobbleSpectrumUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,S,H,W,L,M,A,Q,P,N$. It has no coordinate for hidden biological semantics, stochastic transition laws, quotient codon equality, infinite spectral computation, or a detached Perron oracle.
\end{definition}

\begin{theorem}[Radial wobble spectrum NameCert obligations]
\label{thm:radial-wobble-spectrum-namecert-obligations}
For every accepted $\RadialWobbleSpectrumUp$ carrier $R=(T,S,H,W,L,M,A,Q,P,N)$, the local $\NameCert_{\RadialWobbleSpectrumUp}$ surface consists exactly of boundary-tile coverage admission through $T$, radial-shell exposure through $S$, spectral-hinge exactness through $H$, wobble-edge accounting through $W$, trigger-ledger exposure through $L$, hyperbolic metric boundary reading through $M$, substrate trace preservation through $A$, componentwise transport and replay through $Q$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:radial-wobble-spectrum-carrier}. The accepted packet exposes only the boundary-tile coverage, radial-shell, spectral-hinge, wobble-edge, trigger-ledger, metric, substrate-trace, transport, replay, provenance, and naming rows.

The radial spectrum is carried by $S,H,W$. The shell row records the six states and adjacency counts, the hinge row records the cubic spectral constraint, and the wobble row records the $f_{3}$ contribution before any spectral read may be exported.

The support and geometry rows are $T,L,M,A$. Boundary-tile coverage and trigger algebra bind the finite support surface, while the hyperbolic metric and substrate trace rows preserve the geometric and trace witnesses without adding a hidden spectral oracle.

Finally $Q,P,N$ transport, replay, source, and name the same finite route. Since no coordinate records biological semantics, stochastic transition laws, quotient codon equality, infinite spectral computation, or detached Perron data, none of those objects belongs to the local NameCert surface.
\end{proof}

\begin{theorem}[Radial wobble spectrum trigger nonescape]
\label{thm:radial-wobble-spectrum-trigger-nonescape}
Every concrete radial wobble stability read of an accepted $\RadialWobbleSpectrumUp$ packet factors through
$$
\SixBoundaryTileCoverageUp \longrightarrow \WindowCoverageTriggerAlgebraUp \longrightarrow \HyperbolicMetricUp \longrightarrow \SubstrateTraceInvariantUp .
$$
The radial-shell row $S$, spectral-hinge row $H$, wobble-edge row $W$, and trigger ledger $L$ must be displayed before the packet may claim radial wobble stability.
\end{theorem}
\begin{proof}
Start with the boundary-tile support. The row $T$ supplies finite trigger coverage, and $L$ records the support closure and residue ledger from the trigger algebra.

Next read the radial spectral data. The shell row $S$ gives the six-state adjacency surface, the hinge row $H$ gives the spectral cubic, and $W$ records the wobble self-loop contribution. Removing any one of these rows leaves no carrier coordinate for the claimed radial wobble stability.

Finally read the boundary geometry and trace rows. The hyperbolic metric row $M$ and substrate trace row $A$ preserve the geometric and source-trace witnesses, while $Q,P,N$ transport, replay, source, and name the same route. Thus the packet cannot export a hidden biological table, stochastic transition law, quotient codon equality, infinite spectral computation, or detached Perron oracle.
\end{proof}

\falsifiablePrediction{The packet fails if the spectral-hinge row is removed while the same carrier still claims radial wobble stability.}

\independenceWitness{six_boundary_tile_coverage, window_coverage_trigger_algebra, hyperbolic_metric, substrate_trace_invariant: the carrier has a radial spectral row and trigger ledger not bijective to any single sibling packet.}

The later Lean route for \texttt{BEDC.Derived.RadialWobbleSpectrumUp} must provide explicit $\Nontrivial\ \RadialWobbleSpectrumUp$ and $\FieldFaithful\ \RadialWobbleSpectrumUp$ instances preserving $T,S,H,W,L,M,A,Q,P,N$ as separate displayed fields.

\closureat{RadialWobbleSpectrumUp}{seedStr}

\begin{closurestatus}{\RadialWobbleSpectrumUp}
  \constructivestory{A $\RadialWobbleSpectrumUp$ packet is generated from boundary-tile coverage, radial-shell, spectral-hinge, wobble-edge, trigger-ledger, hyperbolic metric, substrate trace, componentwise transport, displayed replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:radial-wobble-spectrum-carrier}, \autoref{thm:radial-wobble-spectrum-namecert-obligations}, and \autoref{thm:radial-wobble-spectrum-trigger-nonescape} seed the finite radial wobble spectrum packet over boundary-tile, radial-shell, spectral-hinge, wobble-edge, trigger-ledger, geometry, and trace rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological table identity, stochastic evolutionary modeling, quotient codon equality, infinite spectral computation, detached Perron oracles, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, radial-shell exactness, spectral-hinge preservation, wobble-edge accounting, trigger-ledger nonescape, Nontrivial RadialWobbleSpectrumUp, and FieldFaithful RadialWobbleSpectrumUp for BEDC.Derived.RadialWobbleSpectrumUp.}
\end{closurestatus}
