\chapter{A Concrete Naming Certificate for $\CompactMetricClosedBallUp$}
\label{ch:concrete-instances-compact-metric-closed-ball-namecert}
\origin{human}

Following Bishop and Bridges constructive compact metric practice, the $\CompactMetricClosedBallUp$ packet consumes \autoref{ch:concrete-instances-closed-metric-ball-namecert}, \autoref{ch:concrete-instances-compactmetric-namecert}, \autoref{ch:concrete-instances-metric-namecert}, \autoref{ch:concrete-instances-totallybounded-namecert}, \autoref{ch:concrete-instances-completemetric-namecert}, and \autoref{ch:concrete-instances-real-namecert}. It names the finite-net surface of a closed ball inside a displayed compact metric carrier; it does not turn the ball into a host subset, choose a finite subcover, quotient points, or import ambient real completeness.

\begin{definition}[Compact metric closed ball carrier]
\label{def:compact-metric-closed-ball-carrier}
A $\CompactMetricClosedBallUp$ carrier is a finite $\BHist$ packet
$$
K=(X,c,r,M,F,T,C,H,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the $\CompactMetricUp$ source row, carrying the shared metric carrier, the $\TotallyBoundedUp$ finite-net family, and the $\CompleteMetricUp$ complete-limit family over one point classifier.
\item $c$ is the displayed center row carried by the same metric source.
\item $r$ is the $\RealUp$ radius row together with its nonnegative-radius ledger.
\item $M$ is the $\ClosedMetricBallUp$ membership row, recording the comparison $d(c,x)\leq r$ for each displayed point row $x$ that enters the ball surface.
\item $F$ is the finite-net row obtained by restricting a $\TotallyBoundedUp$ ProbeBundle-net request to centers whose coverage route remains inside the closed-ball membership row $M$.
\item $T$ is the total-bounded handoff row that records the tolerance request, bundled centers, membership constructors, coverage distances, and rational comparison ledgers inherited from the compact metric source.
\item $C$ is the complete-limit inheritance row: every carried Cauchy name whose observations remain inside $M$ is routed through the $\CompleteMetricUp$ limit witness of $X$ and returns a limit row still admitted by $M$.
\item $H$ records componentwise $\hsame$ transport for the compact metric source, center, radius, closed-ball membership, finite-net row, total-bounded handoff, complete-limit inheritance, and structural rows.
\item $P$ is the $\Pkg$ provenance over $\CompactMetricClosedBallUp$, $\ClosedMetricBallUp$, $\CompactMetricUp$, $\MetricUp$, $\TotallyBoundedUp$, $\CompleteMetricUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactMetricClosedBallUp}$ row.
\end{enumerate}
The carrier has no coordinate for open-cover compactness, a selected finite subcover, quotient balls, host subsets, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Compact metric closed ball finite-net obligations]
\label{thm:compact-metric-closed-ball-finite-net-obligations}
For an accepted $\CompactMetricClosedBallUp$ carrier $K=(X,c,r,M,F,T,C,H,P,N)$, the local $\NameCert_{\CompactMetricClosedBallUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the compact metric source $X$, center $c$, radius $r$, closed-ball membership row $M$, finite-net row $F$, total-bounded handoff $T$, complete-limit inheritance row $C$, transport row $H$, provenance row $P$, and local naming row $N$;
\item closed-ball membership stability, requiring the comparison $d(c,x)\leq r$ to transport through the metric classifier, the $\RealUp$ radius ledger, and the $\ClosedMetricBallUp$ row $M$;
\item finite-net extraction inside the closed ball, requiring each displayed tolerance request to read bundled centers, membership constructors, coverage distances, and rational comparison rows through $F$ and $T$ without leaving $M$;
\item completion inheritance for carried Cauchy names, requiring every Cauchy thread whose observations are admitted by $M$ to use the $\CompleteMetricUp$ limit-witness family of $X$ and return a limit row still admitted by the same closed-ball comparison;
\item ledger nonescape, stating that no open-cover compactness theorem, selected subcover, quotient ball, host subset, countable-choice selector, or ambient $\RealUp$ completeness row is exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-metric-closed-ball-carrier}. The tuple lists exactly the compact metric source, center, radius, closed-ball membership row, finite-net row, total-bounded handoff, complete-limit inheritance, transport, provenance, and local naming row.

Membership stability is inherited from the displayed metric and closed-ball surfaces. The row $M$ supplies the center-radius comparison, $X$ supplies the metric classifier and distance rows, and the radius row $r$ supplies the $\RealUp$ comparison ledger. Transport through $H$ preserves the same comparison rather than replacing it by a host subset predicate.

For a positive tolerance request, read the $\TotallyBoundedUp$ family inside $X$ and then restrict the resulting ProbeBundle route through $F$. The handoff row $T$ records the bundled centers, membership constructors, coverage distances, and rational comparison ledgers that remain inside the closed-ball membership row $M$.

For a carried Cauchy name, use only the complete-limit family already present in $X$. The inheritance row $C$ states that observations admitted by $M$ are handed to the complete-metric limit witness and that the returned limit row is checked again by the same center-radius comparison.

The remaining structural rows $H,P,N$ transport, source, and name this finite route. Since the carrier inventory contains no open-cover object, subcover selector, quotient-ball constructor, host subset, countable-choice row, or ambient real-completeness row, the listed obligations exhaust the local NameCert surface.
\end{proof}

\closureat{CompactMetricClosedBallUp}{seedStr}

\begin{closurestatus}{\CompactMetricClosedBallUp}
  \constructivestory{A $\CompactMetricClosedBallUp$ packet is generated from a $\CompactMetricUp$ source row, center row, $\RealUp$ radius row, $\ClosedMetricBallUp$ membership row, restricted finite-net row, total-bounded handoff, complete-limit inheritance, componentwise $\hsame$ transport, $\Pkg$ provenance, and local $\NameCert$ naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-metric-closed-ball-carrier} and \autoref{thm:compact-metric-closed-ball-finite-net-obligations} seed the finite closed-ball compact-metric NameCert surface for displayed center-radius packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, choice of subcover, quotient balls, host subsets, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, membership stability, finite-net extraction inside the closed ball, completion inheritance for carried Cauchy names, and ledger nonescape.}
\end{closurestatus}
