\chapter{A Concrete Naming Certificate for $\SchwarzPickDiskContractionUp$}
\label{ch:concrete-instances-schwarz-pick-disk-contraction-namecert}
\origin{human}

Following Schwarz--Pick and Ahlfors' hyperbolic metric reading of holomorphic disk maps, the $\SchwarzPickDiskContractionUp$ packet names disk-map contraction as finite BEDC data. It is grounded in the unit disk carrier of \autoref{ch:concrete-instances-unitdisk-namecert}, the Poincare disk transport route of \autoref{ch:concrete-instances-poincare-disk-phase-transport-namecert}, the hyperbolic metric certificate of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the boundary-dynamics route of \autoref{ch:concrete-instances-denjoy-wolff-boundary-dynamics-namecert}, and the observer-expansion vision of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion}. The packet certifies finite disk-map, metric comparison, boundary refusal, transport, provenance, and NameCert rows; it is not an ambient theorem about all analytic self-maps of a completed complex disk.

\begin{definition}[Schwarz-Pick disk-contraction carrier]
\label{def:schwarz-pick-disk-contraction-carrier}
A $\SchwarzPickDiskContractionUp$ carrier is a finite $\BHist$ packet
$$
S=(D,F,M,K,B,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ coordinate row for displayed source and target disk points.
\item $F$ is the finite disk-map row, recording how the displayed points are transported by the named map.
\item $M$ is the $\HyperbolicMetricUp$ readout row for source and target point pairs.
\item $K$ is the contraction-comparison row stating that the target hyperbolic readout is no larger than the source readout on the displayed pair.
\item $B$ is the boundary-refusal row, separating interior disk-map comparison from Denjoy--Wolff or far-end boundary dynamics.
\item $R$ is the route row linking finite disk coordinates, map transport, metric readout, comparison, and boundary refusal.
\item $H$ stores componentwise $\hsame$ transport for disk coordinates, map rows, metric readouts, comparison rows, boundary refusals, route rows, replay rows, provenance rows, and local naming rows.
\item $C$ stores displayed $\Cont$ replay of the same disk-map and metric-comparison route.
\item $P$ is the $\Pkg$ provenance over $\SchwarzPickDiskContractionUp$, $\UnitDiskUp$, $\PoincareDiskPhaseTransportUp$, $\HyperbolicMetricUp$, $\DenjoyWolffBoundaryDynamicsUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SchwarzPickDiskContractionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,F,M,K,B,R,H,C,P,N$. It has no coordinate for a host holomorphic function space, completed complex disk equality, boundary fixed-point selection, open-cover compactness, or unlogged analytic continuation.
\end{definition}

\begin{theorem}[Schwarz-Pick disk-contraction NameCert obligations]
\label{thm:schwarz-pick-disk-contraction-namecert-obligations}
For every accepted $\SchwarzPickDiskContractionUp$ carrier
$$
S=(D,F,M,K,B,R,H,C,P,N),
$$
the local $\NameCert_{\SchwarzPickDiskContractionUp}$ surface consists exactly of carrier admission for displayed disk coordinates, finite disk-map rows, hyperbolic metric readouts, contraction-comparison rows, boundary-refusal rows, route rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:schwarz-pick-disk-contraction-carrier}. The projection exposes disk coordinates $D$, the finite map row $F$, hyperbolic metric readouts $M$, the contraction comparison $K$, and the boundary-refusal row $B$.

The comparison is read only through $R$. Thus a consumer first displays the source and target disk coordinates, applies the named finite disk-map row, reads the hyperbolic metric on both displayed pairs, and then consumes the no-expansion comparison.

Transport and replay are confined to $H$ and $C$. The provenance and local naming rows $P,N$ record exactly the same route, and the carrier has no coordinate for host analytic function spaces, completed disk equality, boundary fixed-point selection, compactness, or unlogged continuation. These rows therefore exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Schwarz-Pick hyperbolic-metric handoff]
\label{thm:schwarz-pick-disk-contraction-hyperbolic-metric-handoff}
Every hyperbolic-metric consumer of an accepted $\SchwarzPickDiskContractionUp$ packet reaches the contraction verdict only through the ordered handoff
$$
\UnitDiskUp \longrightarrow \PoincareDiskPhaseTransportUp \longrightarrow \HyperbolicMetricUp \longrightarrow \SchwarzPickDiskContractionUp
$$
displayed by $D,F,M,K,B,R,H,C,P,N$. The handoff supplies finite disk-map transport, source and target metric readouts, contraction comparison, boundary refusal, provenance, and NameCert data, and it supplies no ambient analytic self-map theorem or boundary fixed-point conclusion.
\end{theorem}
\begin{proof}
Start with the disk-coordinate row $D$ and the finite map row $F$. These rows display the only source and target points available to the contraction comparison.

The hyperbolic-metric row $M$ then reads the source and target distances on those displayed pairs. The comparison row $K$ consumes those two readouts, while $B$ keeps Denjoy--Wolff boundary dynamics and far-end fixedness outside the interior disk-contraction verdict.

Use the route, transport, and replay rows $R,H,C$ to preserve the same handoff under classifier comparison. The provenance and local naming rows $P,N$ package the finite route, so no host analytic function space, completed disk equality, selected boundary point, compactness argument, or unlogged continuation can enter the metric handoff.
\end{proof}

\closureat{SchwarzPickDiskContractionUp}{seedStr}

\begin{closurestatus}{\SchwarzPickDiskContractionUp}
  \constructivestory{A $\SchwarzPickDiskContractionUp$ packet is generated from UnitDisk coordinates, a finite disk-map row, HyperbolicMetric readouts, a contraction-comparison row, boundary refusal, a route row, componentwise transport, replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:schwarz-pick-disk-contraction-carrier}, \autoref{thm:schwarz-pick-disk-contraction-namecert-obligations}, and \autoref{thm:schwarz-pick-disk-contraction-hyperbolic-metric-handoff} seed the finite disk-contraction carrier, NameCert obligations, and hyperbolic-metric handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not assert a host holomorphic-function theorem, completed disk equality, selected boundary fixed point, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, disk-map exactness, hyperbolic metric readback, contraction comparison, boundary refusal, route preservation, transport stability, replay, provenance, and local naming for BEDC.Derived.SchwarzPickDiskContractionUp.}
\end{closurestatus}
