\chapter{A Concrete Naming Certificate for $\CompleteMetricSpaceUp$}
\label{ch:concrete-instances-complete-metric-space-namecert}
\origin{human}

Following Bishop and Bridges constructive metric completion, the $\CompleteMetricSpaceUp$ packet records a metric carrier together with finite Cauchy-limit service data visible to BEDC consumers. It sits beside the constructive metric surface of \autoref{ch:concrete-instances-bishop-metric-space-namecert}, the separated metric route of \autoref{ch:concrete-instances-complete-separated-metric-namecert}, the regular Cauchy completion unit of \autoref{ch:concrete-instances-regular-cauchy-completion-unit-namecert}, and the Real-facing finite-window route of \autoref{ch:concrete-instances-real-namecert}. The packet supplies an L10 completion-facing neighbour for separated metric, Baire, and completion chapters; it is not a quotient completion, not a selected-limit principle, not countable choice, not host equality, not trichotomy, and not ambient $\RealUp$ completeness.

\begin{definition}[Complete metric-space carrier]
\label{def:complete-metric-space-carrier}
A $\CompleteMetricSpaceUp$ carrier is a finite $\BHist$ packet
$$
K=(M,C,E,L,U,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the underlying $\MetricUp$ row, exposing only the point-name and distance-read surfaces consumed by the packet.
\item $C$ is the $\CompleteMetricUp$ service row, recording that accepted Cauchy requests are answered through displayed limit rows.
\item $E$ is the $\CauchySequenceEquivalenceUp$ boundary row, used only to identify regular Cauchy names that have the same displayed tail behaviour.
\item $L$ is the limit-row ledger. It names the proposed limit point, the convergence-distance rows, and the precision requests consumed by the limit service.
\item $U$ is the uniform Cauchy-service route through $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$; it exposes finite windows, regular rational readbacks, and the terminal Real seal in that order.
\item $H$ stores componentwise $\hsame$ transport for the metric row, completeness row, Cauchy-equivalence boundary, limit ledger, uniform service route, replay, provenance, and local naming rows.
\item $T$ stores displayed $\Cont$ replay from Cauchy-request inspection through $M,C,E,L,U,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MetricUp$, $\CompleteMetricUp$, $\CauchySequenceEquivalenceUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompleteMetricSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,C,E,L,U,H,T,P,N$. It has no coordinate for quotient completions, selected limits, countable choice, host equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Complete metric-space NameCert obligations]
\label{thm:complete-metric-space-namecert-obligations}
For every accepted $\CompleteMetricSpaceUp$ carrier
$$
K=(M,C,E,L,U,H,T,P,N),
$$
the local $\NameCert_{\CompleteMetricSpaceUp}$ surface consists exactly of carrier admission for the displayed metric row $M$, the complete-metric service row $C$, the Cauchy-sequence equivalence boundary $E$, the limit-row ledger $L$, the uniform Cauchy-service route $U$, componentwise transport $H$, displayed replay $T$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:complete-metric-space-carrier}. The projection exposes exactly the metric surface $M$, completeness service $C$, Cauchy-equivalence boundary $E$, limit ledger $L$, uniform service route $U$, and structural rows $H,T,P,N$.

The completeness service is read only through $C$ and $L$. A consumer receives a displayed limit row and convergence-distance ledger, not a quotient completion object or an externally selected representative.

The Cauchy boundary is confined to $E$, while the finite observation route is confined to $U$. Thus tail comparison passes through $\CauchySequenceEquivalenceUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ before any limit read is exported.

Finally $H,T,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for countable choice, host equality, trichotomy, selected limits, quotient completions, or ambient $\RealUp$ completeness, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Complete metric-space Cauchy-limit route]
\label{thm:complete-metric-space-cauchy-limit-route}
Every Cauchy-limit read exported by an accepted $\CompleteMetricSpaceUp$ packet factors through
$$
M\longmapsto E\longmapsto U\longmapsto C,L\longmapsto H,T,P,N .
$$
Consequently separated metric, Baire, and completion-facing consumers may use only the displayed metric row, Cauchy-equivalence boundary, finite-window regular readback route, complete-metric service row, limit ledger, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Begin with the metric row $M$. It supplies the point-name and distance-read surface, but it does not by itself export a limit object.

The Cauchy request then passes through $E$ and $U$. The row $E$ fixes the tail-equivalence boundary for the displayed Cauchy name, while $U$ exposes the finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readbacks, and terminal $\RealUp$ seal needed for the convergence-distance route.

Only after those rows are displayed may the packet read $C$ and $L$. The row $C$ supplies the complete-metric service, and $L$ records the proposed limit point and convergence ledger for the same request.

The rows $H,T,P,N$ preserve that route under transport, replay, provenance, and local naming. Any route that appeals to quotient completions, selected limits, countable choice, host equality, trichotomy, or ambient $\RealUp$ completeness has no displayed coordinate in the carrier.
\end{proof}

\closureat{CompleteMetricSpaceUp}{seedStr}

\begin{closurestatus}{\CompleteMetricSpaceUp}
  \constructivestory{A $\CompleteMetricSpaceUp$ packet is generated from a Metric row, a CompleteMetric service row, a CauchySequenceEquivalence boundary, a limit ledger, a RegSeqRat--StreamName--Real uniform service route, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-metric-space-carrier}, \autoref{thm:complete-metric-space-namecert-obligations}, and \autoref{thm:complete-metric-space-cauchy-limit-route} seed the finite complete metric-space carrier, NameCert obligation surface, and Cauchy-limit route for separated metric, Baire, and completion-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected limits, countable choice, host equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Cauchy-equivalence exactness, finite-window regular readback, complete-metric service confinement, limit-ledger exactness, and non-escape for BEDC.Derived.CompleteMetricSpaceUp.}
\end{closurestatus}
