\chapter{A Concrete Naming Certificate for $\LocatedMetricSpaceUp$}
\label{ch:concrete-instances-located-metric-space-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\LocatedMetricSpaceUp$ packet records a constructive metric space whose distance reads are located before they are consumed by the L10 Phase Real and Completion route. It refines the metric source of \autoref{ch:concrete-instances-metric-namecert} by forcing every distance observation through the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a finite NameCert surface for completion-facing consumers without importing host equality of points, quotient completion, selected limits, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Located metric-space carrier]
\label{def:located-metric-space-carrier}
A $\LocatedMetricSpaceUp$ carrier is a finite $\BHist$ packet
$$
L=(X,M,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the metric-source carrier row, including the local point classifier and the finite point-observation windows on which distance requests are opened.
\item $M$ is the metric source row inherited from \autoref{ch:concrete-instances-metric-namecert}; it displays the distance witness inspected by each accepted pair of point observations.
\item $D$ is the located-distance witness and dyadic tolerance ledger. For each displayed distance request and positive tolerance, it records the finite $\DyadicRatCoreUp$ comparison data that locates the requested distance at that scale.
\item $R$ is the $\RegSeqRatUp$ readback row. It packages the dyadic comparison windows in $D$ as regular rational distance names before any real-facing consumer can read them.
\item $E$ is the $\RealUp$ readback and seal boundary reached only after the metric source, located-distance witness, dyadic tolerance ledger, and regular rational readback have all been displayed.
\item $H$ stores componentwise $\hsame$ transport for point observations, metric source rows, located-distance witnesses, dyadic tolerance ledgers, regular rational readbacks, real seals, replay rows, provenance rows, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from point observations to metric witnesses, from metric witnesses to located dyadic comparisons, from those comparisons to $\RegSeqRatUp$ readbacks, and from the readbacks to the $\RealUp$ seal.
\item $P$ is the $\Pkg$ provenance over $\LocatedMetricSpaceUp$, $\MetricSpaceUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedMetricSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted located metric-space packets only through $X,M,D,R,E,H,C,P,N$. It has no coordinate for host equality of points, quotient real equality, quotient completion, selected limits, total trichotomy of distances, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located metric-space NameCert obligations]
\label{thm:located-metric-space-namecert-obligations}
For every accepted $\LocatedMetricSpaceUp$ carrier
$$
L=(X,M,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedMetricSpaceUp}$ surface consists exactly of carrier admission for the displayed metric source, distance-witness readback through $M$, located-distance and dyadic tolerance accounting through $D$, $\RegSeqRatUp$ readback through $R$, $\RealUp$ seal handoff through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-metric-space-carrier}. The point observations and their local classifier are read from $X$, and every distance request is forced through the metric source row $M$ before locatedness data can be inspected.

The located-distance obligation is the role of $D$. A positive tolerance request reads the dyadic comparison window stored in the $\DyadicRatCoreUp$ ledger, so the packet gives a finite locatedness witness rather than a semantic real-order decision.

The readback obligation then passes through $R$ and $E$. Row $R$ packages the same dyadic windows as regular rational distance names, and row $E$ exposes the real seal only after that regular readback has been displayed.

Finally, $H,C,P,N$ transport, replay, source, and name exactly the same rows. Since the carrier contains no coordinate for host point equality, quotient equality, quotient completion, selected limits, trichotomy, choice, or ambient real completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[L10 located metric-space completion route]
\label{thm:located-metric-space-l10-completion-route}
Every L10 Phase Real and Completion consumer that reads an accepted $\LocatedMetricSpaceUp$ packet factors through
$$
X\longmapsto M\longmapsto D\longmapsto R\longmapsto E
$$
together with $H,C,P,N$. Thus completion-facing distance reads pass through the metric source, located-distance witness, dyadic tolerance ledger, $\RegSeqRatUp$ readback, and $\RealUp$ seal before any completion data is consumed.
\end{theorem}
\begin{proof}
Begin with a completion-facing distance request. The source row $X$ supplies only displayed point observations, so the request must use the metric source row $M$ to obtain the finite distance witness certified by the metric sibling.

Locatedness is supplied by $D$. The dyadic tolerance ledger binds the requested radius to the same metric witness, and it exposes only finite $\DyadicRatCoreUp$ comparison data at the requested scale.

The L10 real-facing route is then determined by $R$ and $E$. The regular rational readback packages the dyadic windows as distance-name data, and the real seal is reached only after that package is visible.

Rows $H,C,P,N$ preserve the same route under transport, replay, provenance, and local naming. Because no excluded quotient, selection, host equality, choice, trichotomy, or ambient-completeness coordinate appears in the carrier, every completion-facing read remains on the displayed L10 route.
\end{proof}

\falsifiablePrediction{Every L10 completion-facing read from a $\LocatedMetricSpaceUp$ packet factors through the displayed metric source, located-distance witness, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, componentwise transport, continuation replay, provenance, and local naming row before completion data is consumed.}

\independenceWitness{metric, dyadicratcore, regseqrat, real: $\LocatedMetricSpaceUp$ is not bijective to any listed sibling because it jointly carries a metric source, located-distance witness, dyadic tolerance ledger, RegSeqRat readback, RealUp seal, componentwise transport, continuation replay, provenance, and local NameCert row.}

\closureat{LocatedMetricSpaceUp}{seedStr}

\begin{closurestatus}{\LocatedMetricSpaceUp}
  \constructivestory{A $\LocatedMetricSpaceUp$ packet is generated from a metric source, located-distance witness, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-metric-space-carrier}, \autoref{thm:located-metric-space-namecert-obligations}, and \autoref{thm:located-metric-space-l10-completion-route} seed the located metric-space carrier and its L10 real-and-completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host equality of points, quotient real equality, quotient completion, selected limits, total trichotomy of distances, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located-distance witness exactness, dyadic tolerance ledger accounting, RegSeqRat readback, RealUp seal handoff, transport replay, and ledger refusal for BEDC.Derived.LocatedMetricSpaceUp.}
\end{closurestatus}
