\chapter{A Concrete Naming Certificate for $\MontelTheoremUp$}
\label{ch:concrete-instances-montel-theorem-namecert}
\origin{human}

Following Montel's theorem in the normal-family tradition, the $\MontelTheoremUp$ packet records only the BEDC finite-window content of constructive normal-family compactness. It binds compact-window rows, local boundedness and equicontinuity ledgers, uniform Cauchy extraction, and holomorphic readback rows over displayed finite charts. The chapter does not claim classical open-cover compactness, countable choice, quotient real or complex equality, selected subsequences, or full analytic compactness. Its sibling route passes through the finite-modulus Arzela--Ascoli surface of \autoref{ch:concrete-instances-arzelaascoli-namecert}, the compact metric and complete metric rows already available in the concrete-instance family, the $\RegSeqRatUp$ and $\DyadicRatCoreUp$ tolerance ledgers, and the holomorphic and complex surfaces when those rows are present.

\begin{definition}[Montel theorem carrier]
\label{def:montel-theorem-carrier}
A $\MontelTheoremUp$ carrier is a finite $\BHist$ packet
$$
M=(K,L,E,U,Q,G,R,D,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact-window row, naming the finite subwindow, metric inspection data, and compact-source certificate used by the family read.
\item $L$ is the local boundedness ledger for the displayed family on the same compact window.
\item $E$ is the equicontinuity ledger, expressed as finite modulus rows over the compact-window inspection schedule.
\item $U$ is the uniform Cauchy extraction row, recording a finite tail window, a subsequence or subnet schedule when already displayed by the source packet, and a dyadic tolerance budget.
\item $Q$ is the uniform-limit readback row over the same compact window.
\item $G$ is the holomorphic or complex-read row, restricted to the displayed chart and consumed only after $K,L,E,U,Q$ have been exposed.
\item $R$ is the $\RegSeqRatUp$ regular-rational readback family for the finite observation windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by the local boundedness, equicontinuity, and uniform Cauchy rows.
\item $Z$ is the terminal complex or real seal row read by the holomorphic surface when such a row is part of the source family.
\item $H$ records componentwise $\hsame$ transport for all displayed rows.
\item $C$ records displayed $\Cont$ replay from compact-window request through local boundedness, equicontinuity, uniform Cauchy extraction, uniform-limit readback, and holomorphic readback.
\item $P$ is the $\Pkg$ provenance over $\MontelTheoremUp$, $\ArzelaAscoliUp$, compact-window and complete-metric rows, $\RegSeqRatUp$, $\DyadicRatCoreUp$, complex or holomorphic surfaces, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MontelTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows and their structural transport, replay, provenance, and local naming data.
\end{definition}

\begin{theorem}[Montel theorem NameCert obligations]
\label{thm:montel-theorem-namecert-obligations}
For every accepted $\MontelTheoremUp$ carrier $M=(K,L,E,U,Q,G,R,D,Z,H,C,P,N)$, the local $\NameCert_{\MontelTheoremUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item compact-window admission for $K$ and agreement of every later row with the same displayed window;
\item local boundedness admission for $L$ over the compact-window schedule;
\item equicontinuity admission for $E$ with dyadic tolerances read from $D$;
\item uniform Cauchy extraction through $U$, with every late-tail comparison served by $R$ and $D$;
\item uniform-limit readback through $Q$ before any holomorphic or complex read in $G$ is exposed;
\item holomorphic readback compatibility, requiring $G$ and $Z$ to consume only the displayed uniform Cauchy and uniform-limit rows;
\item transport, replay, provenance, and naming stability through $H,C,P,N$.
\end{enumerate}
No obligation introduces open-cover compactness, countable choice, quotient real equality, quotient complex equality, a selected analytic limit, or ambient analytic compactness.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:montel-theorem-carrier}. The compact-window row $K$ is the only source of domain inspection data, so every later read is scoped to the same finite compact window.

Local boundedness and equicontinuity are the finite normal-family inputs. The rows $L$ and $E$ expose pointwise bound and finite-modulus data over $K$, while $D$ supplies the dyadic tolerance budget used by both ledgers.

The extraction step is the finite Arzela--Ascoli route. Apply the sibling surface \autoref{ch:concrete-instances-arzelaascoli-namecert} through the displayed rows $K,L,E,U,R,D$ to obtain a uniform Cauchy extraction over the compact window rather than a choice-selected analytic subsequence.

The readback step consumes $Q$ and then $G$. The uniform-limit row is displayed before the holomorphic or complex-read row, so holomorphic readback can use only the finite uniform Cauchy and tolerance surface already named by the carrier.

Finally, $H,C,P,N$ preserve the same row inventory under transport, continuation, provenance, and local naming. Since the carrier has no coordinate for open-cover compactness, countable choice, quotient equality, selected analytic limits, or ambient analytic compactness, the NameCert surface cannot export any such datum.
\end{proof}

\begin{theorem}[Montel theorem finite normal-family criterion]
\label{thm:montel-theorem-finite-normal-family-criterion}
Let $M=(K,L,E,U,Q,G,R,D,Z,H,C,P,N)$ be an accepted $\MontelTheoremUp$ packet. Any consumer claiming a normal-family compactness read from $M$ factors through the finite route
$$
\text{compact window}
\longmapsto
\text{local boundedness and equicontinuity}
\longmapsto
\text{uniform Cauchy extraction}
\longmapsto
\text{uniform-limit readback}
\longmapsto
\text{holomorphic readback}.
$$
Thus the consumer receives compact-window, boundedness, equicontinuity, $\RegSeqRatUp$, $\DyadicRatCoreUp$, uniform Cauchy, uniform-limit, and holomorphic rows as finite BEDC data. It receives no classical open-cover compactness theorem, countable-choice selector, quotient real or complex equality, selected analytic limit, or full analytic compactness assertion.
\end{theorem}
\begin{proof}
Start from the accepted carrier. The only admissible source route begins with $K$, so every compactness-facing consumer first reads the displayed compact-window packet.

Next consume $L$ and $E$. These rows give local boundedness and equicontinuity over that window, with the tolerance budget synchronized by $D$ and the regular readbacks synchronized by $R$.

Now replay $C$ through $U$ and $Q$. The route supplies uniform Cauchy extraction and uniform-limit readback on the same finite window, matching the ContinuousMap and UniformLimit style chapters without selecting an external analytic limit.

Finally consume $G$ and $Z$ only after the uniform-limit row is present. Componentwise transport through $H$ and provenance through $P,N$ preserve the same route, so no forbidden open-cover, choice, quotient-equality, selected-limit, or ambient-compactness coordinate can enter the public read.
\end{proof}

\begin{closurestatus}{\MontelTheoremUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:montel-theorem-carrier}, \autoref{thm:montel-theorem-namecert-obligations}, and \autoref{thm:montel-theorem-finite-normal-family-criterion} seed the finite normal-family route through compact windows, local boundedness, equicontinuity, uniform Cauchy extraction, uniform-limit readback, and holomorphic readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close classical open-cover compactness, countable choice, quotient real equality, quotient complex equality, selected analytic limits, full analytic compactness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-window exactness, local-boundedness and equicontinuity ledgers, uniform Cauchy extraction, holomorphic readback compatibility, and provenance exhaustion for BEDC.Derived.MontelTheoremUp.}
  \constructivestory{A $\MontelTheoremUp$ packet is generated from compact-window rows, local boundedness and equicontinuity ledgers, uniform Cauchy extraction, uniform-limit readback, holomorphic or complex readback, RegSeqRat and DyadicRatCore tolerance rows, transport, replay, provenance, and local NameCert rows.}
\end{closurestatus}
