\chapter{A Concrete Naming Certificate for $\CauchySequenceCompletionUp$}
\label{ch:concrete-instances-cauchy-sequence-completion-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\CauchySequenceCompletionUp$ packet records Cauchy completion data by finite regular-sequence rows rather than by ambient quotient language. It sits after the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the completion handoff of \autoref{ch:concrete-instances-metriccompletion-namecert} and \autoref{ch:concrete-instances-completemetric-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the separated uniqueness boundary of \autoref{ch:concrete-instances-separatedmetric-namecert}. The packet gives Real and Completion consumers one displayed route from finite Cauchy sequence observations to a named completion point.

\begin{definition}[CauchySequenceCompletion carrier]
\label{def:cauchy-sequence-completion-carrier}
A $\CauchySequenceCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(X,S,R,M,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source metric or regular-Cauchy source row whose distance observations are the only metric data available to the packet.
\item $S$ is the $\StreamNameUp$ finite-window row, recording the inspected indices and the request schedule used by the Cauchy read.
\item $R$ is the $\RegSeqRatUp$ readback row on exactly those windows, including the rational approximants and their displayed tail budgets.
\item $M$ is the $\MetricCompletionUp$ handoff row exposing the completion-facing carrier and entry discipline.
\item $L$ is the $\CompleteMetricUp$ limit-service row reached only after $S,R,M$ have been displayed.
\item $E$ is the $\RealUp$ seal row for the completed readback, paired with the $\SeparatedMetricUp$ uniqueness route when two completed names are compared.
\item $H$ records componentwise $\hsame$ transport for the source, window, readback, completion handoff, limit-service, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion request through $X,S,R,M,L,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchySequenceCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\MetricCompletionUp$, $\CompleteMetricUp$, $\RealUp$, $\SeparatedMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchySequenceCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,S,R,M,L,E,H,C,P,N$. It has no coordinate for quotient completion classes, selected representatives, countable choice, host equality of sequences, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CauchySequenceCompletion NameCert obligations]
\label{thm:cauchy-sequence-completion-namecert-obligations}
For every accepted $\CauchySequenceCompletionUp$ carrier $K=(X,S,R,M,L,E,H,C,P,N)$, the local $\NameCert_{\CauchySequenceCompletionUp}$ surface consists exactly of carrier admission for the source metric row, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\MetricCompletionUp$ handoff, $\CompleteMetricUp$ limit row, $\RealUp$ seal, $\SeparatedMetricUp$ uniqueness route, componentwise transport, displayed replay, provenance, and local naming.

Every completion-facing consumer must read these rows in the order
$$
X,S \longmapsto R \longmapsto M,L \longmapsto E \longmapsto H,C,P,N .
$$
No obligation is discharged by a quotient-completion equality, a selected limit, countable choice, host sequence equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-sequence-completion-carrier}. The only source observations are the metric row $X$, the finite windows $S$, and the regular rational readback $R$.

The completion data is downstream of those observations. The row $M$ exposes the $\MetricCompletionUp$ handoff, while $L$ records the $\CompleteMetricUp$ limit service and cannot be read before the displayed windows and readback have been accepted.

The terminal row $E$ is the Real-facing seal. When two completed names are compared, the separated uniqueness boundary is reached through the same displayed rows before any classifier identification is exported.

Finally $H,C,P,N$ transport, replay, source, and name the route. Since the carrier contains no quotient, selected representative, countable-choice schedule, host equality, trichotomy, or ambient Real-completeness coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[CauchySequenceCompletion finite-window route]
\label{thm:cauchy-sequence-completion-finite-window-route}
Every public read of an accepted $\CauchySequenceCompletionUp$ packet that reaches $\MetricCompletionUp$, $\CompleteMetricUp$, or $\RealUp$ must first display the finite $\StreamNameUp$ windows and the $\RegSeqRatUp$ readback used by the Cauchy sequence. If a uniqueness consumer compares two completed reads, it must then pass through the $\SeparatedMetricUp$ zero-distance route before reading equality of the exposed completion names.

Thus the route exports completion data only as a finite window-and-readback handoff:
$$
\StreamNameUp,\ \RegSeqRatUp \longmapsto \MetricCompletionUp,\ \CompleteMetricUp \longmapsto \RealUp,\ \SeparatedMetricUp .
$$
It exports no quotient completion class, selected representative, unrestricted limit selector, host sequence equality, trichotomy, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with a completion-facing request. By \autoref{def:cauchy-sequence-completion-carrier}, the request must open $S$ and $R$ before it can reach either completion row.

The $\MetricCompletionUp$ handoff $M$ and $\CompleteMetricUp$ row $L$ then carry the displayed Cauchy read into the completion surface. The Real seal $E$ is downstream of the same handoff, so a Real-facing read cannot bypass finite windows or regular rational readback.

For uniqueness reads, apply the separated boundary recorded in the carrier. The comparison passes through the zero-distance route of $\SeparatedMetricUp$ before any completed-name identification is public.

The structural rows $H,C,P,N$ preserve this dependency order under transport and replay. No excluded completion, choice, host-equality, trichotomy, or Real-completeness principle is present as a carrier row, so none can be exported by the packet.
\end{proof}

\closureat{CauchySequenceCompletionUp}{seedStr}

\begin{closurestatus}{\CauchySequenceCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-sequence-completion-carrier}, \autoref{thm:cauchy-sequence-completion-namecert-obligations}, and \autoref{thm:cauchy-sequence-completion-finite-window-route} seed the finite Cauchy sequence completion route over StreamName windows, RegSeqRat readback, MetricCompletion and CompleteMetric handoffs, Real seals, separated uniqueness, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, selected representatives, countable choice, host sequence equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window readback, completion handoff, limit-service exposure, Real seal nonescape, separated uniqueness, transport, replay, provenance, and local naming for BEDC.Derived.CauchySequenceCompletionUp.}
  \constructivestory{A $\CauchySequenceCompletionUp$ packet is generated from a source metric row, finite StreamName windows, RegSeqRat readback, MetricCompletion handoff, CompleteMetric limit service, Real seal, SeparatedMetric uniqueness route, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
