\chapter{A Concrete Naming Certificate for $\RealCompletenessDiagonalSelectorUp$}
\label{ch:concrete-instances-real-completeness-diagonal-selector-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\RealCompletenessDiagonalSelectorUp$ packet records the finite diagonal selector route used by the real-completeness corridor of \autoref{ch:visions-real-completeness}. It concretizes the transported stationary diagonal theorem of \autoref{thm:real-completeness-transported-stationary-diagonal} as a NameCert packet over the no-choice selector boundary of \autoref{ch:concrete-instances-choicefreediagonalselector-namecert}, the cofinal tail route of \autoref{ch:concrete-instances-diagonal-tail-selector-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The selector is a displayed Bishop-style regular-Cauchy diagonal construction, not a host choice function, quotient stream, selected completed limit, trichotomy branch, or ambient $\RealUp$ completeness primitive.

\begin{definition}[RealCompletenessDiagonalSelector carrier]
\label{def:real-completeness-diagonal-selector-carrier}
A $\RealCompletenessDiagonalSelectorUp$ carrier is a finite $\BHist$ packet
$$
G=(R,E,T,S,Q,D,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the regular Cauchy source-family row whose finite observations are available through the displayed real-completeness route.
\item $E$ is the $\ChoiceFreeDiagonalSelectorUp$ row, recording the explicit precision request, selected finite window, and refusal of a host choice function.
\item $T$ is the $\DiagonalTailSelectorUp$ row, recording the cofinal tail index and the finite tail-window handoff consumed by the diagonal route.
\item $S$ is the $\StreamNameUp$ window row shared by the selector, tail, and readback requests.
\item $Q$ is the $\RegSeqRatUp$ readback row for the selected diagonal windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the precision budget, selected-window comparisons, and tail-cofinality tolerance entries.
\item $A$ is the terminal $\RealUp$ seal for the selected diagonal representative, available only after $E,T,S,Q,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source-family, selector, tail, window, readback, dyadic ledger, Real seal, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from any diagonal-selector request through $R,E,T,S,Q,D,A$.
\item $P$ is the $\Pkg$ provenance over $\RealCompletenessDiagonalSelectorUp$, $\ChoiceFreeDiagonalSelectorUp$, $\DiagonalTailSelectorUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealCompletenessDiagonalSelectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,E,T,S,Q,D,A,H,C,P,N$. It has no coordinate for host choice, quotient stream equality, selected completed limits, hidden tail oracles, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RealCompletenessDiagonalSelector NameCert obligations]
\label{thm:real-completeness-diagonal-selector-namecert-obligations}
For every accepted $\RealCompletenessDiagonalSelectorUp$ carrier
$$
G=(R,E,T,S,Q,D,A,H,C,P,N),
$$
the local $\NameCert_{\RealCompletenessDiagonalSelectorUp}$ surface consists exactly of carrier admission for the regular Cauchy source family, choice-free finite selector admission, cofinal diagonal-tail routing, shared StreamName window display, RegSeqRat selected-window readback, DyadicRatCore precision and tail-cofinality ledgers, terminal RealUp seal routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, local naming, and non-escape from host choice, quotient streams, selected completed limits, hidden tail oracles, trichotomy, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-completeness-diagonal-selector-carrier}. The source-family row $R$ is only readable through the finite selector and tail rows $E$ and $T$, so no host family choice or completed-limit selector is available before the displayed rows have been opened.

The finite selector stage is explicit. The row $E$ records the precision request and selected window without a host choice function, while $T$ records the cofinal tail handoff used by the same request.

The observation stage is also finite. The shared window row $S$, readback row $Q$, and dyadic ledger $D$ name the StreamName, RegSeqRat, and DyadicRatCore data consumed by the diagonal representative before the Real seal $A$ can be read.

Finally $H,C,P,N$ transport, replay, source, and name exactly this route. Since the carrier has no coordinate for host choice, quotient stream equality, selected completed limits, hidden tail oracles, trichotomy, or ambient Real completeness, none of those objects can be exported by the local certificate.
\end{proof}

\begin{theorem}[RealCompletenessDiagonalSelector non-escape]
\label{thm:real-completeness-diagonal-selector-nonescape}
Every $\RealUp$ or real-completeness-facing consumer of an accepted $\RealCompletenessDiagonalSelectorUp$ carrier factors through the finite route
$$
R \longmapsto E,T \longmapsto S,Q,D \longmapsto A,H,C,P,N .
$$
The transported stationary diagonal row of \autoref{thm:real-completeness-transported-stationary-diagonal} is therefore consumed as finite selector, tail, window, readback, dyadic, seal, transport, replay, provenance, and local naming data, not as host choice, quotient stream equality, selected completed limit, hidden tail oracle, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Start with an accepted packet $G=(R,E,T,S,Q,D,A,H,C,P,N)$. The source-family row $R$ is not a completed real carrier; it becomes visible to a consumer only through the displayed selector and tail rows.

The selector rows $E$ and $T$ fix the finite observation request. The former records the no-choice selection boundary, and the latter records the cofinal tail route that serves the same diagonal window.

The rows $S,Q,D$ then supply the finite StreamName window, RegSeqRat readback, and DyadicRatCore tolerance ledger. The Real seal $A$ is downstream of these rows, so a consumer cannot bypass them to obtain an independent RealUp limit.

Transport and replay preserve the row order under componentwise $\hsame$. The local naming row $N$ therefore exports only the displayed diagonal-selector route and cannot export host choice, quotient streams, selected completed limits, hidden tail oracles, trichotomy, or ambient completeness.
\end{proof}

\closureat{RealCompletenessDiagonalSelectorUp}{seedStr}

\begin{closurestatus}{\RealCompletenessDiagonalSelectorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-completeness-diagonal-selector-carrier}, \autoref{thm:real-completeness-diagonal-selector-namecert-obligations}, and \autoref{thm:real-completeness-diagonal-selector-nonescape} seed the finite Bishop-style diagonal selector route from regular Cauchy source rows through ChoiceFreeDiagonalSelector and DiagonalTailSelector rows to StreamName windows, RegSeqRat readbacks, a DyadicRatCore ledger, and a RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host choice, quotient streams, selected completed limits, hidden tail oracles, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, choice-free selector admission, cofinal tail routing, selected-window readback, dyadic precision and tail-cofinality ledgers, Real-seal routing, transport and replay stability, provenance exhaustion, and non-escape for BEDC.Derived.RealCompletenessDiagonalSelectorUp.}
  \constructivestory{A $\RealCompletenessDiagonalSelectorUp$ packet is generated from a regular Cauchy source-family row, a ChoiceFreeDiagonalSelector row, a DiagonalTailSelector row, shared StreamName windows, RegSeqRat selected-window readbacks, a DyadicRatCore precision ledger, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
