\chapter{A Concrete Naming Certificate for $\CompactCompletionExtensionModulusUp$}
\label{ch:concrete-instances-compact-completion-extension-modulus-namecert}
\origin{human}

Following the Heine--Cantor and Bishop finite-net route, the $\CompactCompletionExtensionModulusUp$ packet records the compact-domain uniform modulus data that completion-extension consumers need before a completed map can be read. It refines the compact-uniform-continuity vision of \autoref{ch:visions-compact-uniform-continuity} into concrete rows over the compact metric packet of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map surface of \autoref{ch:concrete-instances-continuousmap-namecert}, the uniform modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}, the Cauchy lift route of \autoref{ch:concrete-instances-cauchy-completion-lift-namecert}, and the regular completion readback rows of \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names the finite modulus consumer; it does not choose a pointwise selector, quotient a completion, or import ambient compactness or completeness.

\begin{definition}[Compact completion extension modulus carrier]
\label{def:compact-completion-extension-modulus-carrier}
A $\CompactCompletionExtensionModulusUp$ carrier is a finite $\BHist$ packet
$$
K=(Q,G,B,M,L,R,S,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the compact metric finite-net source row, carrying the finite net bundle, located radius rows, and coverage witnesses used by the uniform-modulus fold.
\item $G$ is the $\ContinuousMapUp$ pointwise modulus and graph row, read at bundled centers of the compact net.
\item $B$ is the $\RatUp$ lower-bound fold row, recording the finite rational radius comparison that produces a tolerance-only precision history.
\item $M$ is the $\UniformModulusUp$ consumer row opened by $Q,G,B$.
\item $L$ is the $\CauchyCompletionLiftUp$ route row, exposing the modulus handoff before any completion-extension consumer reads lifted map data.
\item $R$ is the $\RegSeqRatUp$ readback row for regular Cauchy approximants opened by the completion consumer.
\item $S$ is the $\StreamNameUp$ finite-window row used to compare the compact-net source data with the completion readback.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger carrying dyadic radii, error budgets, and transported comparison rows.
\item $E$ is the terminal $\RealUp$ seal, visible only after $Q,G,B,M,L,R,S,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the compact source, graph, lower-bound fold, uniform modulus, lift route, readback, window, dyadic ledger, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
Q,G,B \longmapsto M,L \longmapsto R,S,D \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactCompletionExtensionModulusUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\RatUp$, $\UniformModulusUp$, $\CauchyCompletionLiftUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactCompletionExtensionModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,G,B,M,L,R,S,D,E,H,C,P,N$. It has no coordinate for a global point selector, quotient completion equality, selected completed representatives, host function equality, open-cover compactness, choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Compact modulus preservation for completion-extension consumers]
\label{thm:compact-completion-extension-modulus-preservation}
Let
$$
K=(Q,G,B,M,L,R,S,D,E,H,C,P,N)
$$
be an accepted $\CompactCompletionExtensionModulusUp$ carrier. Any completion-extension consumer that reads the compact-domain map must preserve the uniform modulus row $M$ produced from the finite-net source $Q$, pointwise graph row $G$, and rational lower-bound fold $B$ before it can inspect the $\CauchyCompletionLiftUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows.
\end{theorem}
\begin{proof}
Project the carrier. The compact finite-net source row $Q$, continuous graph row $G$, and rational lower-bound fold row $B$ are displayed before the uniform modulus row $M$.

The completion-extension consumer then enters through $L$. Since $L$ is downstream of $M$, the completion-facing map is read as data carrying the compactly produced uniform modulus rather than as a host function on completed representatives.

The readback rows $R,S,D,E$ preserve this dependency order. Regular approximants, finite stream windows, dyadic tolerance budgets, and the terminal Real seal are all opened after the modulus handoff, so none can replace it with quotient completion equality or a selected limit.

The structural rows $H,C,P,N$ only transport, replay, source, and name the same route. Therefore point selectors, host equality, open-cover compactness, choice, and ambient $\RealUp$ completeness remain outside the accepted consumer surface.
\end{proof}

\closureat{CompactCompletionExtensionModulusUp}{seedStr}

\begin{closurestatus}{\CompactCompletionExtensionModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-completion-extension-modulus-carrier} and \autoref{thm:compact-completion-extension-modulus-preservation} seed the compact finite-net uniform-modulus route consumed by completion-extension packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close point selector choice, quotient completion equality, selected completed representatives, host function equality, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net visibility, continuous-map pointwise modulus readback, rational lower-bound fold stability, uniform-modulus preservation, completion-lift routing, regular readback, finite-window stability, dyadic tolerance stability, Real seal non-escape, and ledger exhaustion for BEDC.Derived.CompactCompletionExtensionModulusUp.}
  \constructivestory{A $\CompactCompletionExtensionModulusUp$ packet is generated from CompactMetric finite-net source rows, a ContinuousMap pointwise graph row, a RatUp lower-bound fold, a UniformModulus consumer row, a CauchyCompletionLift route, RegSeqRat readback, StreamName windows, a DyadicRatCore tolerance ledger, a Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
