\chapter{A Concrete Naming Certificate for $\BooleanTriggerLatticeUp$}
\label{ch:concrete-instances-boolean-trigger-lattice-namecert}
\origin{ai}

The $\BooleanTriggerLatticeUp$ packet realizes the Boolean trigger closure lattice of \autoref{def:philosophy-boolean-trigger-closure} and \autoref{thm:philosophy-rank-spectral-trigger-lattice-theorem} as finite BEDC NameCert data. It sits over the finite truth-tag discipline of \autoref{ch:concrete-instances-bool-namecert}, the six-boundary-tile coverage route of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, and the trigger-algebra sibling surface of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}. The packet names Boolean support, rank, meet, join, spectral table, transport, replay, provenance, and local naming rows; it is not a biological code oracle, stochastic evolution model, host powerset lattice, quotient codon semantics, or infinite trigger search.

\begin{definition}[BooleanTriggerLattice carrier]
\label{def:boolean-trigger-lattice-carrier}
A $\BooleanTriggerLatticeUp$ carrier is a finite $\BHist$ packet
$$
T=(B,S,R,J,K,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the finite $\BoolUp$ tag row for present, absent, covered, uncovered, full-trigger, and non-trigger reads.
\item $S$ is the six-boundary support row, read from $\SixBoundaryTileCoverageUp$ and carrying the displayed coordinates $\{s_{1},f_{1},s_{2},f_{2}\}$.
\item $R$ is the rank row, naming the finite support union $J(B)$ and the rank $r(B)$ of the source vision.
\item $J$ is the join-trigger row, recording median closure of a union as support union.
\item $K$ is the meet-trigger row, recording intersection of trigger closures as support intersection.
\item $O$ is the observed table row, carrying the finite size, cubical, spectral, threshold, and singleton-trigger reads displayed in the source vision.
\item $H$ records componentwise $\hsame$ transport for Boolean tags, support rows, rank rows, join rows, meet rows, observed table rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from each accepted trigger read through $B,S,R,J,K,O,H$.
\item $P$ is the $\Pkg$ provenance over $\BooleanTriggerLatticeUp$, $\BoolUp$, $\SixBoundaryTileCoverageUp$, $\WindowCoverageTriggerAlgebraUp$, the source vision of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BooleanTriggerLatticeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,S,R,J,K,O,H,C,P,N$. It has no coordinate for host powersets, biological-code truth, stochastic dynamics, quotient codon equality, hidden spectral computation, or unbounded trigger enumeration.
\end{definition}

\begin{theorem}[BooleanTriggerLattice NameCert obligations]
\label{thm:boolean-trigger-lattice-namecert-obligations}
For every accepted $\BooleanTriggerLatticeUp$ carrier $T=(B,S,R,J,K,O,H,C,P,N)$, the local $\NameCert_{\BooleanTriggerLatticeUp}$ surface consists exactly of Boolean tag admission, six-boundary support exposure, finite rank exposure, join-trigger exposure, meet-trigger exposure, observed table exposure, componentwise transport, displayed replay, provenance, and local naming.

The future Lean TasteGate plan for this packet requires $\Nontrivial\ \BooleanTriggerLatticeUp$ and $\FieldFaithful\ \BooleanTriggerLatticeUp$ so that $B,S,R,J,K,O,H,C,P,N$ remain separate displayed fields rather than a collapsed tag.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:boolean-trigger-lattice-carrier}. The rows $B,S,R,J,K,O$ expose the Boolean tags, boundary support, rank, join, meet, and observed table before any consumer can read a trigger-lattice conclusion.

The join and meet rows are finite. The row $J$ reads support union from the source vision, while $K$ reads support intersection. Both rows depend on the same six-boundary support surface and therefore cannot be replaced by an ambient powerset lattice.

The observed table row is also displayed. It records the finite rank-size, cubical, spectral, threshold, and singleton-trigger data already present in the vision file, but it does not add a stochastic model or a hidden spectral oracle.

Finally $H,C,P,N$ preserve the same displayed route. Since no host powerset, biological truth oracle, quotient codon equality, stochastic dynamics, or unbounded trigger enumeration is a carrier coordinate, the local NameCert obligations are exactly the listed rows.
\end{proof}

\falsifiablePrediction{An accepted $\BooleanTriggerLatticeUp$ read is refuted if its full-trigger, rank, meet, or join decision can be produced without the displayed Boolean tags, six-boundary support row, finite rank row, observed table row, transport, replay, provenance, and local naming.}

\independenceWitness{bool, six-boundary-tile-coverage, window-coverage-trigger-algebra, boolean-trigger source vision: none is bijective with $\BooleanTriggerLatticeUp$ because the packet jointly carries Boolean tags, six-boundary support, trigger rank, join rows, meet rows, observed rank-spectral table data, transport, replay, provenance, and local naming.}

\closureat{BooleanTriggerLatticeUp}{seedStr}

\begin{closurestatus}{\BooleanTriggerLatticeUp}
  \constructivestory{A $\BooleanTriggerLatticeUp$ packet is generated from BoolUp tag rows, six-boundary support rows, finite rank rows, join-trigger rows, meet-trigger rows, observed rank-spectral table rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:boolean-trigger-lattice-carrier} and \autoref{thm:boolean-trigger-lattice-namecert-obligations} seed the finite Boolean trigger-lattice NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim biological-code truth, stochastic evolutionary dynamics, host powerset lattices, quotient codon equality, hidden spectral computation, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Boolean tag exposure, support-rank exposure, meet and join rows, observed table exposure, Nontrivial BooleanTriggerLatticeUp, and FieldFaithful BooleanTriggerLatticeUp for BEDC.Derived.BooleanTriggerLatticeUp.}
\end{closurestatus}
