\chapter{A Concrete Naming Certificate for $\RegularCauchyAlgebraCoherenceUp$}
\label{ch:concrete-instances-regular-cauchy-algebra-coherence-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyAlgebraCoherenceUp$ packet records the finite BEDC route by which regular rational Cauchy addition and product share one source surface, one window discipline, one dyadic arithmetic ledger, and one terminal real-name seal. It refines the binary route of \autoref{ch:concrete-instances-cauchy-sequence-algebra-namecert} by isolating the coherence rows that make the addition and product certificates descend through the same $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyAdditionUp$, $\RegularCauchyProductUp$, and $\RealUp$ interfaces. The packet supplies later Real algebra consumers with a finite $\NameCert$ surface for shared operation descent, without importing quotient Cauchy classes, host real arithmetic, selected limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[RegularCauchyAlgebraCoherence carrier]
\label{def:regular-cauchy-algebra-coherence-carrier}
A $\RegularCauchyAlgebraCoherenceUp$ carrier is a finite $\BHist$ packet
$$
K=(L,R,W,D,A,M,S,T,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $L$ and $R$ are the left and right $\RegSeqRatUp$ source rows.
\item $W$ is the shared $\StreamNameUp$ window row used to inspect both sources at the requested tolerance scale.
\item $D$ is the $\DyadicRatCoreUp$ ledger containing the displayed slack conversions, endpoint arithmetic, comparison checks, addition budgets, product budgets, and magnitude bounds.
\item $A$ is the $\RegularCauchyAdditionUp$ descent row. It consumes only $L,R,W,D$ and returns the regular addition readback.
\item $M$ is the $\RegularCauchyProductUp$ descent row. It consumes only $L,R,W,D$ and returns the regular product readback.
\item $S$ is the $\RealUp$ operation seal. It exposes an addition or product real-name handoff only after the corresponding regular readback row has been displayed.
\item $T$ records componentwise $\hsame$ transport for the sources, window, dyadic ledger, addition row, product row, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an operation request through $L,R,W,D,A,M,S,T,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyAlgebraCoherenceUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyAdditionUp$, $\RegularCauchyProductUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyAlgebraCoherenceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $L,R,W,D,A,M,S,T,C,P,N$. It has no coordinate for quotient-stream equality, a host real operation, a selected limit, countable choice, trichotomy, or an ambient $\RealUp$ completeness principle.
\end{definition}

\begin{theorem}[RegularCauchyAlgebraCoherence NameCert obligations]
\label{thm:regular-cauchy-algebra-coherence-namecert-obligations}
For every accepted $\RegularCauchyAlgebraCoherenceUp$ carrier
$$
K=(L,R,W,D,A,M,S,T,C,P,N),
$$
the local $\NameCert_{\RegularCauchyAlgebraCoherenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier exposure for the two $\RegSeqRatUp$ sources, the shared $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, the $\RegularCauchyAdditionUp$ row, the $\RegularCauchyProductUp$ row, the $\RealUp$ seal, transport, replay, provenance, and local naming;
\item source coherence, requiring addition and product to read the same ordered source pair $L,R$;
\item window coherence, requiring both operation rows to inspect the source pair only through $W$;
\item dyadic ledger coherence, requiring every addition and product estimate to consume only the displayed arithmetic and comparison entries of $D$;
\item descent separation, requiring $A$ to carry the addition descent and $M$ to carry the product descent while sharing the same upstream rows;
\item operation sealing, requiring $S$ to expose a $\RealUp$ handoff only after the selected operation row has produced its regular readback;
\item stability and replay, requiring $T$ and $C$ to preserve the full route $L,R,W,D,A,M,S,P,N$ under $\hsame$ and $\Cont$ without adding any excluded analytic or quotient principle.
\end{enumerate}
No RegularCauchyAlgebraCoherence NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier exposure is the projection list in \autoref{def:regular-cauchy-algebra-coherence-carrier}. The displayed data rows are exactly $L,R,W,D,A,M,S$, and the structural rows are exactly $T,C,P,N$.

Source and window coherence follow from the single source pair and the single window row. Since both $A$ and $M$ cite $L,R,W$ as their upstream surface, there is no second source pair or hidden window service from which either operation can draw.

The dyadic ledger row gives the common arithmetic budget. Addition consumes it through $A$, product consumes it through $M$, and the theorem asserts only those two separated descent rows over the same ledger.

Finally, $S,T,C,P,N$ close the finite certificate surface. The seal exposes only regular readback data as a $\RealUp$ handoff, while transport, replay, provenance, and local naming preserve the displayed route. None of the excluded principles has a carrier coordinate.
\end{proof}

\begin{theorem}[RegularCauchyAlgebraCoherence operation seal]
\label{thm:regular-cauchy-algebra-coherence-operation-seal}
Every $\RealUp$ consumer of an accepted $\RegularCauchyAlgebraCoherenceUp$ carrier reads regular Cauchy addition or product data through the finite route
$$
L,R \longmapsto W \longmapsto D \longmapsto A,M \longmapsto S \longmapsto T,C,P,N .
$$
Consequently the consumer obtains the two regular source rows, the shared stream window, the dyadic ledger, the addition descent row, the product descent row, the operation seal, transport, replay, provenance, and local naming, and obtains no quotient Cauchy class, host real operation, selected limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a $\RealUp$ operation request. By \autoref{def:regular-cauchy-algebra-coherence-carrier}, the request has access to the source rows only as $L,R$, and it has access to their finite observations only through $W$.

The arithmetic step is then forced through $D$. Addition reads $A$, product reads $M$, and both descent rows are downstream of the same source, window, and dyadic ledger rows recorded in \autoref{thm:regular-cauchy-algebra-coherence-namecert-obligations}.

The seal $S$ is the only Real-facing coordinate. It can expose an addition or product handoff only after the corresponding regular readback is displayed, and the rows $T,C,P,N$ preserve that same finite route. Therefore a $\RealUp$ consumer has no coordinate from which to extract any excluded quotient, host, choice, order, or completeness datum.
\end{proof}

\begin{theorem}[RegularCauchyAlgebraCoherence non-escape]
\label{thm:regular-cauchy-algebra-coherence-nonescape}
Let $K=(L,R,W,D,A,M,S,T,C,P,N)$ be an accepted $\RegularCauchyAlgebraCoherenceUp$ carrier. Any algebraic fact exported from $K$ is a rowwise consequence of the displayed regular source rows, shared stream window, dyadic ledger, operation descent rows, Real seal, transport, replay, provenance, and local naming rows. It is not a quotient Cauchy class, host real addition, host real multiplication, selected limit, countable-choice datum, trichotomy datum, or ambient $\RealUp$ completeness datum.
\end{theorem}
\begin{proof}
Inspect the carrier rows. The data-bearing coordinates are exactly $L,R,W,D,A,M,S$, and the structural coordinates are exactly $T,C,P,N$.

An exported addition fact must pass through $A$ after the common source, window, and ledger rows are displayed. An exported product fact must pass through $M$ after the same upstream rows are displayed. A Real-facing fact must then pass through $S$.

The remaining rows preserve only that route. Componentwise $\hsame$ transport and displayed $\Cont$ replay cannot introduce a quotient relation, host operation, selected limit, choice principle, trichotomy principle, or completeness principle, while $\Pkg$ and $\NameCert$ record only the finite packet. Hence every exported algebraic fact is confined to the listed rows.
\end{proof}

\closureat{RegularCauchyAlgebraCoherenceUp}{seedStr}

\begin{closurestatus}{\RegularCauchyAlgebraCoherenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-algebra-coherence-carrier}, \autoref{thm:regular-cauchy-algebra-coherence-namecert-obligations}, \autoref{thm:regular-cauchy-algebra-coherence-operation-seal}, and \autoref{thm:regular-cauchy-algebra-coherence-nonescape} seed the finite coherence route for addition and product descent over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyAdditionUp$, $\RegularCauchyProductUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient Cauchy classes, host real operations, selected limits, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, source coherence, window coherence, dyadic ledger coherence, descent separation, operation sealing, stability, replay, provenance, local naming, and non-escape for BEDC.Derived.RegularCauchyAlgebraCoherenceUp.}
  \constructivestory{A $\RegularCauchyAlgebraCoherenceUp$ packet is generated from two $\RegSeqRatUp$ source rows, one shared $\StreamNameUp$ window, one $\DyadicRatCoreUp$ ledger, $\RegularCauchyAdditionUp$ and $\RegularCauchyProductUp$ descent rows, a $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
