\chapter{A Concrete Naming Certificate for $\LeibnizSeriesTestUp$}
\label{ch:concrete-instances-leibniz-series-test-namecert}
\origin{human}

Following Bishop and Bridges' constructive treatment of alternating series, the $\LeibnizSeriesTestUp$ packet records the classical alternating-series tail-bound route as finite BEDC data before any completion-facing consumer may read a regular rational handoff or a real seal. It refines the convergence-test surface of \autoref{ch:concrete-instances-alternating-series-test-namecert}, uses the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, opens only the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, measures tail tolerances through the dyadic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and terminates at the real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite Leibniz tail-bound route; it does not import selected sums, quotient series equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[LeibnizSeriesTest carrier]
\label{def:leibniz-series-test-carrier}
A $\LeibnizSeriesTestUp$ carrier is a finite $\BHist$ packet
$$
L_{\lambda}=(S,\Sigma,M,T,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ source row, listing the finite partial-sum and summand windows opened by the request.
\item $\Sigma$ is the finite alternating-sign row, recording the parity and sign entries visible on the displayed windows.
\item $M$ is the monotone magnitude row, recording nonnegative dyadic magnitude reads and their finite monotonicity comparisons on the inspected tail.
\item $T$ is the tail-bound schedule, assigning each requested dyadic tolerance to a displayed tail index whose next visible magnitude is within that tolerance.
\item $Q$ is the $\AlternatingSeriesTestUp$ handoff row, accepting the source, alternating-sign, monotone-magnitude, and tail-bound rows as the local convergence-test face.
\item $R$ is the $\RegSeqRatUp$ readback row for the displayed partial-sum stream after the handoff row has been displayed.
\item $E$ is the terminal $\RealUp$ seal row, available only after $S,\Sigma,M,T,Q,R$ have been read.
\item $H$ records componentwise $\hsame$ transport for the source, sign, magnitude, tail-bound, handoff, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from any Leibniz-series-test request through $S,\Sigma,M,T,Q,R,E$.
\item $P$ is the $\Pkg$ provenance over $\LeibnizSeriesTestUp$, $\AlternatingSeriesTestUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LeibnizSeriesTestUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,\Sigma,M,T,Q,R,E,H,C,P,N$. It has no coordinate for selected sums, quotient series equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[LeibnizSeriesTest NameCert obligations]
\label{thm:leibniz-series-test-namecert-obligations}
For every accepted $\LeibnizSeriesTestUp$ carrier
$$
L_{\lambda}=(S,\Sigma,M,T,Q,R,E,H,C,P,N),
$$
the local $\NameCert_{\LeibnizSeriesTestUp}$ surface consists exactly of finite source-window admission, alternating-sign display, monotone magnitude display, dyadic tail-bound scheduling, $\AlternatingSeriesTestUp$ handoff, $\RegSeqRatUp$ readback, terminal $\RealUp$ seal routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, local naming, and non-escape from selected sums, quotient series equality, countable choice, trichotomy, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:leibniz-series-test-carrier}. The only source observations are the finite windows in $S$, and the only sign information is the displayed parity ledger $\Sigma$.

The tail estimate is finite. The row $M$ gives the visible monotone magnitude comparisons, while $T$ records the tail index chosen for each requested dyadic tolerance. The handoff row $Q$ then accepts exactly those source, sign, magnitude, and tail-bound rows through the $\AlternatingSeriesTestUp$ surface.

The completion-facing route is also finite. The regular readback $R$ may be read only after $Q$, and the terminal seal $E$ receives only $R$ together with the displayed source, sign, magnitude, and tail-bound route.

Finally $H,C,P,N$ transport, replay, source, and name that same route. Since no carrier coordinate stores a selected sum, quotient series equality, countable-choice schedule, trichotomy premise, or ambient completeness theorem, none of those objects can be exported by the local certificate.
\end{proof}

\begin{theorem}[LeibnizSeriesTest Real-seal nonescape]
\label{thm:leibniz-series-test-real-seal-nonescape}
Every $\RealUp$ seal-facing read exported by an accepted $\LeibnizSeriesTestUp$ carrier factors through the finite route
$$
S,\Sigma,M,T \longmapsto Q \longmapsto R \longmapsto E,H,C,P,N .
$$
Thus the Leibniz tail-bound route reaches the terminal Real seal only through displayed alternating signs, monotone magnitudes, dyadic tail bounds, the alternating-series-test handoff, and regular rational readback; it does not expose selected sums, quotient series equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted packet $L_{\lambda}=(S,\Sigma,M,T,Q,R,E,H,C,P,N)$. A Real-facing consumer must first open the displayed source windows $S$, because no partial-sum observation is available outside those windows.

The sign and magnitude checks are then forced by $\Sigma$ and $M$. The tail-bound schedule $T$ is the only row that converts a requested dyadic tolerance into a displayed tail index, and the handoff row $Q$ records that those finite rows enter the alternating-series-test surface.

The regular rational handoff is $R$, and the Real seal is $E$. Since $E$ is available only after $R$ and the finite handoff route have been displayed, any seal-facing read stays inside the named route.

The transport, replay, provenance, and local naming rows preserve that route componentwise. Hence the exported boundary cannot contain selected sums, quotient series equality, countable choice, trichotomy, or ambient Real completeness.
\end{proof}

\closureat{LeibnizSeriesTestUp}{seedStr}

\begin{closurestatus}{\LeibnizSeriesTestUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:leibniz-series-test-carrier}, \autoref{thm:leibniz-series-test-namecert-obligations}, and \autoref{thm:leibniz-series-test-real-seal-nonescape} seed the finite Leibniz tail-bound route from displayed alternating signs and monotone magnitudes through RegSeqRat readback to a RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected sums, quotient series equality, countable choice, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, sign and magnitude display, tail-bound scheduling, alternating-series-test handoff, regular rational readback, Real-seal routing, transport and replay stability, provenance exhaustion, and non-escape for BEDC.Derived.LeibnizSeriesTestUp.}
  \constructivestory{A $\LeibnizSeriesTestUp$ packet is generated from finite StreamName windows, an alternating-sign row, monotone magnitude row, dyadic tail-bound schedule, AlternatingSeriesTestUp handoff, RegSeqRatUp readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
