\chapter{A Concrete Naming Certificate for $\CoverageRankAlgebraUp$}
\label{ch:concrete-instances-coverage-rank-algebra-namecert}
\origin{ai}

The $\CoverageRankAlgebraUp$ packet realizes the coverage-rank algebra of \autoref{thm:philosophy-coverage-rank-algebra-theorem} as finite BEDC NameCert data. It consumes the six-boundary tile coverage route of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the Boolean trigger lattice of \autoref{ch:concrete-instances-boolean-trigger-lattice-namecert}, the window coverage-trigger algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}, and the finite observation fold of \autoref{ch:concrete-instances-finite-observation-fold-namecert}. The packet binds boundary-tile coverage, rank, trigger support, classifier stability, replay, provenance, and local naming rows; it is not a biological code oracle, stochastic transition model, quotient codon space, hidden global support lattice, or infinite trigger search.

\begin{definition}[Coverage-rank algebra carrier]
\label{def:coverage-rank-algebra-carrier}
A $\CoverageRankAlgebraUp$ carrier is a finite $\BHist$ packet
$$
K=(B,R,T,L,F,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the consumed $\SixBoundaryTileCoverageUp$ row exposing the six boundary-tile coverage coordinates and their visible support faces.
\item $R$ is the rank row, recording the finite support-union rank read from the coverage-rank algebra vision.
\item $T$ is the boundary-trigger support row, carrying the visible trigger support whose equality or inequality is tested by the classifier.
\item $L$ is the consumed $\BooleanTriggerLatticeUp$ row naming Boolean meet, join, and support-rank comparisons over the same visible boundary supports.
\item $F$ is the consumed $\FiniteObservationFoldUp$ row that bounds every algebra read by a displayed finite observation fold and its omitted-tail ledger.
\item $Q$ is the consumed $\WindowCoverageTriggerAlgebraUp$ row, carrying the finite closure, blocker, threshold, and residue-facing algebra rows used by downstream trigger consumers.
\item $H$ records componentwise $\hsame$ transport for coverage, rank, trigger support, Boolean lattice, finite fold, trigger algebra, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a boundary-trigger coverage request through $B,R,T,L,F,Q,H$.
\item $P$ is the $\Pkg$ provenance over $\CoverageRankAlgebraUp$, $\SixBoundaryTileCoverageUp$, $\BooleanTriggerLatticeUp$, $\WindowCoverageTriggerAlgebraUp$, $\FiniteObservationFoldUp$, the source vision of \autoref{thm:philosophy-coverage-rank-algebra-theorem}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CoverageRankAlgebraUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,R,T,L,F,Q,H,C,P,N$. It has no coordinate for hidden biological semantics, stochastic dynamics, quotient codon equality, global support completion, host rank lattices, or infinite trigger enumeration.
\end{definition}

\begin{theorem}[Coverage-rank algebra NameCert obligations]
\label{thm:coverage-rank-algebra-namecert-obligations}
For every accepted $\CoverageRankAlgebraUp$ carrier $K=(B,R,T,L,F,Q,H,C,P,N)$, the local $\NameCert_{\CoverageRankAlgebraUp}$ surface consists exactly of boundary-tile coverage through $B$, rank exposure through $R$, boundary-trigger support through $T$, Boolean trigger-lattice comparison through $L$, finite observation folding through $F$, coverage-trigger algebra handoff through $Q$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.

The proposed Lean follow-up for \texttt{BEDC.Derived.CoverageRankAlgebraUp} must provide explicit $\Nontrivial\ \CoverageRankAlgebraUp$ and $\FieldFaithful\ \CoverageRankAlgebraUp$ instances preserving $B,R,T,L,F,Q,H,C,P,N$ as separate displayed fields.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:coverage-rank-algebra-carrier}. The rows $B,R,T,L,F,Q$ expose boundary-tile coverage, rank, trigger support, Boolean comparison, finite observation folding, and trigger-algebra handoff before any algebra consumer can read a coverage-rank conclusion.

The classifier is rank-sensitive but support-visible. Equal-rank reads are admitted only through the displayed trigger support row $T$ and the Boolean comparison row $L$, so a consumer cannot collapse unequal boundary-trigger supports into one stable classifier row.

The finite observation fold $F$ bounds every read, and $Q$ supplies only the already displayed coverage-trigger algebra route. The rows $H,C,P,N$ preserve, replay, source, and name this finite route, leaving hidden biological semantics, stochastic dynamics, quotient codon equality, global support completion, host rank lattices, and infinite trigger enumeration outside the carrier.
\end{proof}

\begin{theorem}[Coverage-rank boundary-trigger separation]
\label{thm:coverage-rank-algebra-boundary-trigger-separation}
Let $K=(B,R,T,L,F,Q,H,C,P,N)$ and $K'=(B',R',T',L',F',Q',H',C',P',N')$ be accepted $\CoverageRankAlgebraUp$ packets. If the rank rows $R$ and $R'$ display the same finite rank but the boundary-trigger support rows $T$ and $T'$ expose different support, then a classifier-stable identification of $K$ and $K'$ is refused unless it also supplies a displayed transport row through $L,L',F,F',Q,Q'$ preserving the unequal support evidence. Thus equal rank alone never determines equality of the coverage-rank algebra packet.
\end{theorem}
\begin{proof}
Read the two carriers. The rank rows $R,R'$ and trigger-support rows $T,T'$ are separate coordinates, so equality of rank does not erase the displayed support data.

The Boolean lattice and finite-fold rows $L,L',F,F'$ are the only rows that compare support and bound the observation. A classifier-stable identification must therefore preserve these rows before the trigger-algebra handoff can be read.

Finally $Q,Q',H,H',C,C',P,P',N,N'$ replay and name the same finite route. Since no host rank lattice or hidden global support completion is a carrier coordinate, equal rank with unequal boundary-trigger support remains separated at the packet boundary.
\end{proof}

\falsifiablePrediction{Any accepted $\CoverageRankAlgebraUp$ packet that identifies equal rank with unequal boundary-trigger support without displaying the Boolean trigger-lattice, finite observation fold, coverage-trigger algebra, transport, replay, provenance, and local naming rows violates classifier stability.}

\independenceWitness{six-boundary-tile-coverage, boolean-trigger-lattice, window-coverage-trigger-algebra, finite-observation-fold: $\CoverageRankAlgebraUp$ is not bijective to any listed sibling because it jointly carries boundary-tile coverage, rank, boundary-trigger support, Boolean comparison, finite observation fold, coverage-trigger algebra handoff, transport, replay, provenance, and local naming as one packet.}

\closureat{CoverageRankAlgebraUp}{seedStr}

\begin{closurestatus}{\CoverageRankAlgebraUp}
  \constructivestory{A $\CoverageRankAlgebraUp$ packet is generated from six-boundary tile coverage rows, rank rows, boundary-trigger support rows, Boolean trigger-lattice comparison rows, finite observation fold rows, coverage-trigger algebra rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:coverage-rank-algebra-carrier}, \autoref{thm:coverage-rank-algebra-namecert-obligations}, and \autoref{thm:coverage-rank-algebra-boundary-trigger-separation} seed the finite coverage-rank algebra packet over boundary-tile coverage, rank, trigger support, classifier, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological-code truth, stochastic transition laws, quotient codon equality, hidden global support lattices, host rank lattices, infinite trigger search, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, rank exposure, boundary-trigger separation, classifier stability, Nontrivial CoverageRankAlgebraUp, and FieldFaithful CoverageRankAlgebraUp for BEDC.Derived.CoverageRankAlgebraUp.}
\end{closurestatus}
