\chapter{Cauchy Condensation Theorem NameCert Construction}
\label{ch:concrete-instances-cauchy-condensation-theorem-namecert}
\origin{human}

Following Cauchy and Bishop--Bridges constructive analysis, the $\CauchyCondensationTheoremUp$ packet records the theorem-level NameCert surface that turns a monotone nonnegative $\RealSeriesUp$ tail into the dyadic block series and back through Cauchy criteria. It sits after the dyadic-block packet of \autoref{ch:concrete-instances-cauchycondensation-namecert}, the comparison-test surface of \autoref{ch:concrete-instances-cauchy-condensation-test-namecert}, the Real-series carrier of \autoref{ch:concrete-instances-cauchy-condensation-real-series-namecert}, and the finite dyadic partition ledger of \autoref{ch:concrete-instances-dyadic-partition-namecert}. The packet is a theorem certificate over displayed tails, block ledgers, and Cauchy handoff rows; it is not a host summability principle, a quotient of infinite series, a selected sum, countable choice, arbitrary trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy condensation theorem carrier]
\label{def:cauchy-condensation-theorem-carrier}
A $\CauchyCondensationTheoremUp$ carrier is a finite $\BHist$ packet
$$
K=(A,M,D,B,G,Q,U,V,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the monotone nonnegative $\RealSeriesUp$ source row, read only through finite term windows and partial-sum windows.
\item $M$ is the monotone-tail ledger, recording the nonnegativity row, decreasing transport, and the finite tail cut from which the theorem is applied.
\item $D$ is the $\DyadicPartitionUp$ block schedule, listing the powers of two, block endpoints, and finite block intervals used by the theorem.
\item $B$ is the original block-sum ledger, storing the finite sums of $A$ over the dyadic intervals named by $D$.
\item $G$ is the condensed-series row, displaying the dyadic terms $2^n a_{2^n}$ on the same block schedule.
\item $Q$ is the blockwise comparison ledger, recording the lower and upper estimates that monotonicity supplies between $B$ and $G$.
\item $U$ is the original-series Cauchy criterion row, expressed through displayed partial-sum windows of $A$.
\item $V$ is the condensed-series Cauchy criterion row, expressed through displayed partial-sum windows of $G$.
\item $R$ is the $\RegSeqRatUp$ readback row for the original and condensed partial-sum windows.
\item $E$ is the $\RealUp$ seal-facing row reached only after the Cauchy criterion handoff has passed through $U,V,R$.
\item $H$ records componentwise $\hsame$ transport for the source, monotone ledger, dyadic schedule, block sums, condensed terms, comparison ledger, Cauchy rows, readback row, seal row, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each finite tail request through the dyadic blocks, comparison ledger, Cauchy criteria, regular readback, and seal-facing row.
\item $P$ is the $\Pkg$ provenance over $\CauchyCondensationTheoremUp$, $\RealSeriesUp$, $\CauchyCondensationUp$, $\CauchyCondensationTestUp$, $\CauchyCondensationRealSeriesUp$, $\DyadicPartitionUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCondensationTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $A,M,D,B,G,Q,U,V,R,E,H,C,P,N$. It has no coordinate for a host infinite sum, quotient equality of series, selected endpoint, countable choice, an arbitrary trichotomy split, or an ambient completeness theorem.
\end{definition}

\begin{definition}[Blockwise Cauchy comparison classifier]
\label{def:cauchy-condensation-theorem-blockwise-classifier}
Two accepted $\CauchyCondensationTheoremUp$ carriers are blockwise Cauchy equivalent when their displayed $\RealSeriesUp$ source rows, monotone-tail ledgers, dyadic schedules, original block sums, condensed terms, comparison rows, original and condensed Cauchy criterion rows, regular readbacks, seal-facing rows, transports, continuations, provenance, and local names are pairwise $\hsame$ through the rows named in \autoref{def:cauchy-condensation-theorem-carrier}. Equivalence is not allowed to inspect an unlisted host limit, a quotient of streams, or a chosen infinite sum.
\end{definition}

\begin{theorem}[Cauchy condensation theorem NameCert obligations]
\label{thm:cauchy-condensation-theorem-namecert-obligations}
For every accepted $\CauchyCondensationTheoremUp$ carrier $K=(A,M,D,B,G,Q,U,V,R,E,H,C,P,N)$, the local $\NameCert_{\CauchyCondensationTheoremUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed fourteen-row packet;
\item monotone nonnegative source exposure through $A$ and $M$;
\item dyadic block scheduling through $D$ and original block-sum formation through $B$;
\item condensed dyadic-term formation through $G$;
\item blockwise tail comparison through $Q$, using only monotone transport on displayed finite windows;
\item original-to-condensed Cauchy transport through $U,V,R$;
\item $\RealUp$ seal exposure through $E$ only after the Cauchy handoff has reached the regular readback row;
\item transport stability, continuation replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
No obligation row asserts host summability, a selected infinite sum, quotient equality of real streams, countable choice, arbitrary trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier $K=(A,M,D,B,G,Q,U,V,R,E,H,C,P,N)$. The carrier row exposes exactly the monotone Real-series source, monotone-tail ledger, dyadic block schedule, original block sums, condensed terms, comparison ledger, two Cauchy criterion rows, regular readback, seal-facing row, and structural rows.

The source and classifier obligations are finite. The rows $A$ and $M$ provide nonnegativity and decreasing behavior only on displayed term windows, while \autoref{def:cauchy-condensation-theorem-blockwise-classifier} permits comparison only through the carrier coordinates named in \autoref{def:cauchy-condensation-theorem-carrier}.

The dyadic block ledger is then read. The schedule $D$ fixes the inspected powers of two and finite intervals, $B$ records the original block sums on those intervals, and $G$ records the condensed terms $2^n a_{2^n}$ on the same indices.

Monotone transport enters only through $Q$. Each block comparison is a finite estimate between rows already displayed by $A,M,D,B,G$, so the theorem-level packet does not appeal to an infinite selector of blocks or to host equality of series.

Finally the Cauchy-convergence handoff is read through $U,V,R,E$. The original and condensed Cauchy criterion rows route the two partial-sum tails into the same regular readback boundary before the $\RealUp$ seal row is visible. The rows $H,C,P,N$ preserve, replay, source, and name that route, so the listed obligations exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{An accepted $\CauchyCondensationTheoremUp$ consumer that claims theorem-level condensation without reading the monotone source row, dyadic block schedule, original block sums, condensed terms, blockwise comparison ledger, Cauchy criterion rows, and $\RegSeqRatUp$ handoff refutes the carrier surface.}

\independenceWitness{cauchycondensation, cauchy-condensation-test, cauchy-condensation-real-series, dyadic-partition, realseries, regseqrat, real: no listed sibling supplies the whole fourteen-row theorem packet $K=(A,M,D,B,G,Q,U,V,R,E,H,C,P,N)$, because each sibling contributes only a dyadic block, comparison-test, Real-series, partition, readback, or seal face while this chapter binds the theorem-level equivalence through blockwise comparison and Cauchy handoff.}

\closureat{CauchyCondensationTheoremUp}{seedStr}

\begin{closurestatus}{\CauchyCondensationTheoremUp}
  \constructivestory{A $\CauchyCondensationTheoremUp$ packet is generated from a monotone nonnegative RealSeries source row, a monotone-tail ledger, a DyadicPartition block schedule, original block sums, condensed dyadic terms, a blockwise comparison ledger, original and condensed Cauchy criterion rows, RegSeqRat readback, a RealUp seal-facing row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-condensation-theorem-carrier}, \autoref{def:cauchy-condensation-theorem-blockwise-classifier}, and \autoref{thm:cauchy-condensation-theorem-namecert-obligations} seed the theorem-level dyadic block carrier, classifier, monotone transport ledger, and Cauchy-convergence handoff for monotone nonnegative real series.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host summability, quotient equality of series, selected sums, countable choice, arbitrary trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode BEDC.Derived.CauchyCondensationTheoremUp and prove carrier admission, blockwise classifier stability, monotone dyadic transport, the block ledger, and the Cauchy criterion handoff.}
\end{closurestatus}
