\chapter{A Concrete Naming Certificate for $\CauchySequenceOrderCompletenessUp$}
\label{ch:concrete-instances-cauchy-sequence-order-completeness-namecert}
\origin{human}

Following Bishop--Bridges constructive real analysis, the $\CauchySequenceOrderCompletenessUp$ packet records the finite boundary where an ordered Cauchy sequence can be read as a completion-facing real-order object without quotient equality, selected limits, or an ambient completeness primitive. It sits over the ordered sequence route of \autoref{ch:concrete-instances-cauchy-sequence-order-namecert}, the algebra route of \autoref{ch:concrete-instances-cauchy-sequence-algebra-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, and the complete-metric boundary of \autoref{ch:concrete-instances-completemetric-namecert}. The packet names the ordered Cauchy completion boundary as displayed BEDC data; it is not a quotient completion, not a selected representative, and not a host real-order completeness theorem.

\begin{definition}[Cauchy sequence order completeness carrier]
\label{def:cauchy-sequence-order-completeness-carrier}
A $\CauchySequenceOrderCompletenessUp$ carrier is a finite $\BHist$ packet
$$
K=(O,A,R,S,D,E,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the $\CauchySequenceOrderUp$ row, carrying the finite order-comparison requests and monotone-tail witnesses available to the completion boundary.
\item $A$ is the $\CauchySequenceAlgebraUp$ row, carrying the finite algebraic closure operations used by the same tail windows.
\item $R$ is the $\RegSeqRatUp$ readback row generated from the ordered algebraic Cauchy sequence data.
\item $S$ is the $\StreamNameUp$ finite-window row through which the inspected sequence entries and comparison windows are read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic radii, split tolerances, and comparison budgets used by $O,A,R,S$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the regular rational readback and dyadic ledger have been displayed.
\item $M$ is the $\CompleteMetricUp$ boundary row, recording the finite completion-facing metric handoff visible to consumers after $O,A,R,S,D,E$.
\item $H$ stores componentwise $\hsame$ transport for the order, algebra, regular readback, stream window, dyadic ledger, real seal, complete-metric boundary, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from ordered Cauchy requests through algebraic closure, stream windows, regular rational readback, dyadic comparison, real sealing, and the complete-metric handoff.
\item $P$ is the $\Pkg$ provenance over $\CauchySequenceOrderCompletenessUp$, $\CauchySequenceOrderUp$, $\CauchySequenceAlgebraUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CompleteMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchySequenceOrderCompletenessUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $O,A,R,S,D,E,M,H,C,P,N$. It contains no coordinate for quotient completion equality, selected representatives, countable choice, host real equality, ambient $\RealUp$ completeness, or a bridge-checked standard completion object.
\end{definition}

\begin{theorem}[Cauchy sequence order completeness NameCert obligations]
\label{thm:cauchy-sequence-order-completeness-namecert-obligations}
For every accepted $\CauchySequenceOrderCompletenessUp$ carrier $K=(O,A,R,S,D,E,M,H,C,P,N)$, the local $\NameCert_{\CauchySequenceOrderCompletenessUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed order, algebra, regular readback, stream-window, dyadic tolerance, real-seal, complete-metric boundary, transport, replay, provenance, and local naming rows;
\item order-algebra compatibility, requiring every completion-facing order comparison to read the same $\CauchySequenceOrderUp$ row $O$ and $\CauchySequenceAlgebraUp$ row $A$ before any regular rational readback is exposed;
\item regular-name handoff, requiring the $\RegSeqRatUp$ row $R$ to be generated from the displayed stream windows $S$ and dyadic tolerance ledger $D$;
\item real-seal and metric-boundary exposure, requiring the $\RealUp$ row $E$ and $\CompleteMetricUp$ row $M$ to appear only after $O,A,R,S,D$ have been transported through $H$ and replayed through $C$;
\item ledger nonescape, excluding quotient completion equality, selected representatives, countable choice, host real equality, ambient real completeness, and bridge checking from the local carrier.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-sequence-order-completeness-carrier}. The accepted inventory is exactly $O,A,R,S,D,E,M,H,C,P,N$, so carrier admission and classifier comparison are finite.

The order and algebra rows are read together. A completion-facing order request cannot inspect the regular rational row until the displayed order row $O$, algebra row $A$, stream windows $S$, and dyadic comparison ledger $D$ have been exposed.

The real seal and complete-metric boundary are downstream. The row $E$ seals the regular rational readback through $\RealUp$, while $M$ records only the finite completion-facing metric handoff after the same route has been transported and replayed.

Finally inspect the excluded coordinates. Since the carrier has no quotient equality, selected representative, countable-choice, host equality, ambient-completeness, or bridge-checking row, the local NameCert cannot export any of those objects.
\end{proof}

\begin{theorem}[Cauchy sequence order completeness nonescape]
\label{thm:cauchy-sequence-order-completeness-nonescape}
Every completion-facing consumer of an accepted $\CauchySequenceOrderCompletenessUp$ carrier must traverse the displayed route
$$
\CauchySequenceOrderUp,\ \CauchySequenceAlgebraUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp,\ \CompleteMetricUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert
$$
before it can expose an ordered completion boundary. The route exports no quotient completion, no selected limit representative, no countable-choice schedule, no host real equality, no ambient $\RealUp$ completeness theorem, and no bridge claim.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $K=(O,A,R,S,D,E,M,H,C,P,N)$. The only order source is $O$, and the only algebraic closure source is $A$; both are upstream of the finite stream windows and regular rational readback.

Read $S,R,D$ next. These rows expose finite observations, regular rational data, and dyadic tolerance budgets before any real or metric boundary can be inspected.

The terminal rows $E$ and $M$ are reached only through the componentwise transports $H$ and displayed replay $C$. The provenance row $P$ and local naming row $N$ source exactly that route.

Since the carrier inventory has no quotient, selector, choice, host equality, ambient completeness, or bridge coordinate, every ordered completion read remains inside the displayed finite BEDC route.
\end{proof}

\falsifiablePrediction{Every $\CauchySequenceOrderCompletenessUp$ completion-facing read factors through displayed CauchySequenceOrder, CauchySequenceAlgebra, StreamName, RegSeqRat, DyadicRatCore, RealUp, CompleteMetric, transport, replay, provenance, and local naming rows before exposing an ordered completion boundary.}

\independenceWitness{cauchy-sequence-order, cauchy-sequence-algebra, regseqrat, streamname, dyadicratcore, real, completemetric: $\CauchySequenceOrderCompletenessUp$ is not bijective to any listed sibling because it jointly carries ordered tail comparisons, algebraic Cauchy closure, regular rational readback, finite stream windows, dyadic tolerance rows, a Real seal, and a complete-metric handoff in one finite completion-boundary packet.}

\closureat{CauchySequenceOrderCompletenessUp}{seedStr}

\begin{closurestatus}{\CauchySequenceOrderCompletenessUp}
  \constructivestory{A $\CauchySequenceOrderCompletenessUp$ packet is generated from CauchySequenceOrder and CauchySequenceAlgebra rows, finite StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealUp seal, a CompleteMetric boundary row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-sequence-order-completeness-carrier}, \autoref{thm:cauchy-sequence-order-completeness-namecert-obligations}, and \autoref{thm:cauchy-sequence-order-completeness-nonescape} seed the finite ordered Cauchy completion boundary over order, algebra, regular rational, stream, dyadic, real, and complete-metric rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, countable choice, host real equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, order-algebra compatibility, regular-name handoff, real-seal exposure, complete-metric boundary exposure, and ledger nonescape for BEDC.Derived.CauchySequenceOrderCompletenessUp.}
\end{closurestatus}
