\chapter{A Concrete Naming Certificate for $\CompactUniformOscillationUp$}
\label{ch:concrete-instances-compact-uniform-oscillation-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and the Heine--Cantor finite-net route, the $\CompactUniformOscillationUp$ packet records the finite data by which compact metric source rows and uniform-modulus rows produce bounded target-distance oscillation witnesses. It consumes the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map graph of \autoref{ch:concrete-instances-continuousmap-namecert}, the uniform-modulus ledger of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the target distance surface of \autoref{ch:concrete-instances-metric-namecert}. The packet is a finite oscillation-bound consumer for compact-uniform-continuity routes; it is not an open-cover compactness principle, a selected supremum, host extensionality of functions, or a global image-compactness theorem.

\begin{definition}[Compact uniform oscillation carrier]
\label{def:compact-uniform-oscillation-carrier}
A $\CompactUniformOscillationUp$ carrier is a finite $\BHist$ packet
$$
O=(K,F,M,D,W,H,C,P,L)
$$
with the following visible rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row, recording the compact finite-net observations and metric comparison rows on the source space.
\item $F$ is the $\ContinuousMapUp$ graph row, recording the finite graph evaluations and local continuity reads used by the compact-uniform route.
\item $M$ is the $\UniformModulusUp$ ledger, recording tolerance requests, source-radius responses, and the modulus rows obtained from compact finite nets.
\item $D$ is the target-distance row, a $\MetricUp$ or $\RealMetricUp$ readback ledger for the distances between displayed output observations.
\item $W$ is the finite $\ProbeBundle$ oscillation-witness row, recording source net points, paired source observations within the modulus radius, and the resulting target-distance bounds.
\item $H$ records componentwise $\hsame$ transport for the compact source, continuous graph, uniform modulus, target-distance ledger, oscillation witnesses, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from each finite target-oscillation request through
$$
K,F,M,D,W \longmapsto H,P,L .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactUniformOscillationUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\MetricUp$, $\RealMetricUp$, $\ProbeBundle$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\CompactUniformOscillationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a selected supremum of image diameters, open-cover compactness, quotient equality of maps, choice-selected net refinements, trichotomy, or host function extensionality.
\end{definition}

\begin{theorem}[Compact uniform oscillation NameCert obligations]
\label{thm:compact-uniform-oscillation-namecert-obligations}
For an accepted $\CompactUniformOscillationUp$ carrier
$$
O=(K,F,M,D,W,H,C,P,L),
$$
the local $\NameCert_{\CompactUniformOscillationUp}$ surface consists exactly of carrier admission for the displayed rows, compact finite-net exposure for $K$, continuous graph exposure for $F$, uniform-modulus accounting for $M$, target-distance accounting for $D$, finite oscillation-witness exposure for $W$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $L$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-uniform-oscillation-carrier}. The accepted packet displays the compact metric source, continuous-map graph, uniform-modulus ledger, target-distance ledger, finite witness row, transport row, replay row, provenance row, and local name.

The compact-uniform route is read from $K,F,M$. A consumer first receives finite compact-net observations, then the displayed continuous graph rows, and then the tolerance-only modulus ledger built over those observations.

The oscillation estimate is read from $D$ and $W$. Target-distance comparisons are visible only through $D$, while $W$ stores the finite witness pairs whose source separation is small enough for the modulus row.

Finally $H,C,P,L$ transport, replay, source, and name the same route. Because no coordinate stores a selected supremum, open-cover compactness, quotient equality, choice-selected refinements, trichotomy, or host function extensionality, those principles are outside the local certificate surface.
\end{proof}

\begin{theorem}[Compact uniform oscillation modulus handoff]
\label{thm:compact-uniform-oscillation-modulus-handoff}
Every bounded image-diameter or equicontinuity-facing read accepted by a $\CompactUniformOscillationUp$ carrier factors through
$$
\CompactMetricUp,\ \ContinuousMapUp,\ \UniformModulusUp,\ \MetricUp,\ \ProbeBundle,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Equivalently, a downstream consumer may inspect compact finite-net data $K$, continuous graph data $F$, the uniform-modulus ledger $M$, target-distance rows $D$, finite oscillation witnesses $W$, and structural rows $H,C,P,L$, but it cannot bypass them by selecting a supremum, importing open-cover compactness, or comparing maps by host extensionality.
\end{theorem}
\begin{proof}
Apply \autoref{thm:compact-uniform-oscillation-namecert-obligations}. It forces every oscillation-facing request to open $K,F,M,D,W$ before the structural rows are available.

The finite-net part is controlled by $K$ and $M$. Compactness is consumed as displayed net data and a tolerance-only modulus ledger, not as an external open-cover principle.

The target estimate is controlled by $D$ and $W$. The witness row stores the paired observations whose target distances are bounded, and the distance ledger records the corresponding metric readback.

Transport, replay, provenance, and naming through $H,C,P,L$ preserve exactly that route. Hence later bounded-image or equicontinuity packets receive a finite oscillation-bound handoff and no selected supremum or host-level function equality.
\end{proof}

\falsifiablePrediction{Every $\CompactUniformOscillationUp$ oscillation read factors through one CompactMetric finite-net source row, one ContinuousMap graph row, one UniformModulus ledger, one target Metric or RealMetric distance row, one finite ProbeBundle oscillation-witness row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{compactmetric, continuousmap, uniformmodulus, metric, realmetric: $\CompactUniformOscillationUp$ is not bijective to any listed sibling because it jointly carries compact finite-net data, continuous graph data, a uniform-modulus ledger, target-distance readback, finite oscillation witnesses, and the transport/replay/provenance rows tying them into an oscillation-bound packet.}

\closureat{CompactUniformOscillationUp}{seedStr}

\begin{closurestatus}{\CompactUniformOscillationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-oscillation-carrier}, \autoref{thm:compact-uniform-oscillation-namecert-obligations}, and \autoref{thm:compact-uniform-oscillation-modulus-handoff} seed the finite compact-uniform oscillation packet over compact metric source rows, continuous graph rows, uniform-modulus ledgers, target-distance readbacks, finite witnesses, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected suprema, open-cover compactness, image compactness, host function extensionality, choice-selected net refinements, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net exposure, continuous graph exposure, uniform-modulus accounting, target-distance accounting, oscillation-witness stability, transport stability, replay stability, and ledger non-escape for BEDC.Derived.CompactUniformOscillationUp.}
  \constructivestory{A $\CompactUniformOscillationUp$ packet is generated from one CompactMetric finite-net source row, one ContinuousMap graph row, one UniformModulus ledger, one target-distance row, one finite ProbeBundle oscillation-witness row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
