\chapter{A Concrete Naming Certificate for $\LipschitzFunctionUp$}
\label{ch:concrete-instances-lipschitz-function-namecert}
\origin{human}

Following Kelley metric-space practice and Bishop--Bridges constructive analysis, the $\LipschitzFunctionUp$ packet records a function only through displayed metric rows, a graph ledger, and a carried bound. It sits between the source and target metric surface of \autoref{ch:concrete-instances-metric-namecert}, the terminal real-bound seal of \autoref{ch:concrete-instances-real-namecert}, the graph discipline of \autoref{ch:concrete-instances-continuousmap-namecert}, and the tolerance export of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet is a finite NameCert connector for uniform-continuity and completion-facing consumers; it does not import host function extensionality, quotient map equality, choice of representatives, or ambient completeness.

\begin{definition}[Lipschitz function carrier]
\label{def:lipschitz-function-carrier}
A $\LipschitzFunctionUp$ carrier is a finite $\BHist$ packet
$$
F=(X,Y,G,K,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source $\MetricSpaceUp$ row and $Y$ is the target $\MetricSpaceUp$ row.
\item $G$ is the $\ContinuousMapUp$ graph row carrying the function-read relation from $X$ to $Y$.
\item $K$ is the nonnegative $\RealUp$ Lipschitz-constant row.
\item $D$ is the distance-inequality ledger recording every displayed comparison between a source-distance request and the corresponding target-distance response.
\item $H$ records componentwise $\hsame$ transport for source points, target points, graph rows, bound rows, distance ledgers, continuation rows, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from source metric requests through $G,K,D$ to target metric responses and uniform-modulus reads.
\item $P$ is the $\Pkg$ provenance over $\LipschitzFunctionUp$, $\MetricSpaceUp$, $\RealUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LipschitzFunctionUp}$ row.
\end{enumerate}
The classifier accepts only packets whose target-distance reads are sourced by $G$ and bounded through the same $K,D$ ledger. It has no coordinate for a host function object, quotient equality of maps, selected representatives, differentiability, compactness, or completeness of either metric space.
\end{definition}

\begin{theorem}[Lipschitz function NameCert obligations]
\label{thm:lipschitz-function-namecert-obligations}
For every accepted $\LipschitzFunctionUp$ carrier $F=(X,Y,G,K,D,H,C,P,N)$, the local $\NameCert_{\LipschitzFunctionUp}$ surface consists exactly of carrier admission, componentwise classifier comparison, Lipschitz-bound exactness, graph-to-distance replay, uniform-modulus export, transport stability, provenance sourcing, and local naming through the displayed rows $X,Y,G,K,D,H,C,P,N$.

No obligation row is stored outside the carrier, and no exported read depends on host function extensionality, quotient map equality, selected representatives, countable choice, differentiability, compactness, or ambient metric completeness.
\end{theorem}
\begin{proof}
Project the carrier. The only analytic rows are the source metric $X$, target metric $Y$, graph row $G$, Lipschitz constant $K$, and distance-inequality ledger $D$.

The classifier comparison is componentwise over those rows and over $H,C,P,N$. Bound exactness follows because a target-distance read has to pass through the graph row and then through the displayed comparison stored in $D$ against the same constant $K$.

The uniform-modulus export reads no further object. Transport $H$ and replay $C$ preserve the same graph, constant, and inequality rows, while $P$ and $N$ only source and name the route. Since the carrier contains none of the excluded host objects, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Lipschitz function uniform-continuity handoff]
\label{thm:lipschitz-function-uniform-continuity-handoff}
Every $\UniformModulusUp$, $\UniformContinuityUp$, or $\ContinuousMapUp$ consumer of an accepted $\LipschitzFunctionUp$ carrier receives its source-tolerance route only after the packet has displayed the source metric $X$, target metric $Y$, graph row $G$, Lipschitz constant $K$, distance-inequality ledger $D$, and replay rows $H,C,P,N$. The handoff is a finite BEDC modulus route, not a rereading of a host Lipschitz proof.
\end{theorem}
\begin{proof}
Start from the carrier and its NameCert obligations. The graph row $G$ supplies the only function-read surface, while $K$ and $D$ supply the only bound and distance-comparison surface.

A uniform-modulus request therefore cannot bypass the displayed inequality ledger. It first fixes the target-distance request in $Y$, reads the bound row $K$, and then uses $D$ to return the corresponding source-distance request in $X$.

The continuation and transport rows preserve this order. Hence uniform-continuity and continuous-map consumers receive a finite modulus handoff through $X,Y,G,K,D,H,C,P,N$, with no host function proof or selected representative added.
\end{proof}

\begin{theorem}[Lipschitz function completion nonescape]
\label{thm:lipschitz-function-completion-nonescape}
Every completion-facing consumer of an accepted $\LipschitzFunctionUp$ carrier remains confined to the displayed metric rows, graph row, bound row, distance-inequality ledger, transport, replay, provenance, and local name rows. Reading a complete source or target metric in another packet does not turn $F$ into a completed function-space object, a quotient of uniformly continuous maps, a selected extension, or a statement about limits outside $X,Y,G,K,D,H,C,P,N$.
\end{theorem}
\begin{proof}
The packet carries only two metric rows and a graph-bound ledger between them. Completion-facing reads may reuse those metric rows, but no completed function-space coordinate is present in the carrier.

The distance ledger $D$ is also local. It records comparisons for the displayed graph row and constant, and replay through $C$ keeps those comparisons attached to the same source and target metric requests.

Thus a completion consumer can transport the finite Lipschitz route but cannot manufacture quotient maps, selected extensions, host limits, or ambient completeness claims. The exported surface remains exactly $X,Y,G,K,D,H,C,P,N$.
\end{proof}

\closureat{LipschitzFunctionUp}{seedStr}

\begin{closurestatus}{\LipschitzFunctionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lipschitz-function-carrier}, \autoref{thm:lipschitz-function-namecert-obligations}, \autoref{thm:lipschitz-function-uniform-continuity-handoff}, and \autoref{thm:lipschitz-function-completion-nonescape} seed the finite Lipschitz-function route from metric, graph, real-bound, distance-ledger, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, host function extensionality, quotient map equality, selected extensions, differentiability, compactness, completed function spaces, countable choice, or ambient completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier comparison, Lipschitz-bound exactness, graph-to-distance replay, uniform-modulus export, transport stability, provenance sourcing, and local NameCert rows for BEDC.Derived.LipschitzFunctionUp.}
  \constructivestory{A $\LipschitzFunctionUp$ packet is generated from source and target metric rows, a ContinuousMap graph row, a RealUp Lipschitz constant, a distance-inequality ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
\end{closurestatus}
