\chapter{A Concrete Naming Certificate for $\MetricCompletionFunctorialityUp$}
\label{ch:concrete-instances-metric-completion-functoriality-namecert}
\origin{human}

Following Bishop and Bridges constructive metric completion theory, the $\MetricCompletionFunctorialityUp$ packet records the finite route by which a uniformly controlled metric map induces a map between displayed completion packets. It sits after the metric completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the functor-facing Cauchy completion surface of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, the universal extension ledger of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, the dense-extension route of \autoref{ch:concrete-instances-dense-isometry-extension-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}. The packet names functoriality only as displayed source, target, map, Cauchy-control, completion-entry, universal-property, comparison, transport, replay, provenance, and local NameCert rows; it is not a quotient-completion equality, a selected limit map, function extensionality, countable choice, or ambient completeness.

\begin{definition}[MetricCompletionFunctoriality carrier]
\label{def:metric-completion-functoriality-carrier}
A $\MetricCompletionFunctorialityUp$ carrier is a finite $\BHist$ packet
$$
F=(X,Y,G,A,E,U,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source $\MetricUp$ row whose completion-facing names are inspected.
\item $Y$ is the target $\MetricUp$ row whose completion packet receives the induced read.
\item $G$ is the finite graph row of the underlying map from source names to target names.
\item $A$ is the Cauchy-control ledger, recording the modulus or window transfer by which $\StreamNameUp$ observations of $X$ yield $\RegSeqRatUp$ readbacks over $Y$.
\item $E$ is the completion-entry row, naming the $\MetricCompletionUp$ source and target entries used by the induced map.
\item $U$ is the $\CompletionUniversalPropertyUp$ row through which the extension and uniqueness read is consumed.
\item $S$ is the separated comparison row, requiring induced target reads to compare only through the displayed separated metric or dense-extension surface.
\item $H$ records componentwise $\hsame$ transport for the source metric, target metric, graph, Cauchy-control, completion-entry, universal-property, separated-comparison, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a source completion request through $G,A,E,U,S,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionUp$, $\CauchyCompletionFunctorialityUp$, $\CompletionUniversalPropertyUp$, $\DenseIsometryExtensionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\MetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricCompletionFunctorialityUp}$ row.
\end{enumerate}
The carrier contains no coordinate for quotient completions, selected representatives of Cauchy classes, host function equality, countable-choice selection, an ambient completed metric space, or a second extension principle outside $U$.
\end{definition}

\begin{theorem}[MetricCompletionFunctoriality NameCert obligations]
\label{thm:metric-completion-functoriality-namecert-obligations}
For every accepted $\MetricCompletionFunctorialityUp$ carrier $F=(X,Y,G,A,E,U,S,H,C,P,N)$, the local $\NameCert_{\MetricCompletionFunctorialityUp}$ surface consists exactly of carrier admission for the source metric, target metric, finite map graph, Cauchy-control ledger, completion-entry row, universal-property row, separated comparison row, componentwise transport, continuation replay, provenance, and local naming. Every induced completion read must pass through the $\StreamNameUp$ and $\RegSeqRatUp$ control recorded in $A$, the $\MetricCompletionUp$ entry row $E$, the $\CompletionUniversalPropertyUp$ ledger $U$, and the separated comparison row $S$ before the local name $N$ is exposed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-functoriality-carrier}. The rows $X,Y,G,A,E,U,S,H,C,P,N$ are the whole public packet, so source and target metric data, the map graph, the Cauchy-control ledger, completion entries, universal-property data, and separated comparison are all displayed before the induced map is consumed.

The Cauchy-control row supplies the constructive handoff. A source completion request first reads finite $\StreamNameUp$ windows, then the $\RegSeqRatUp$ readback governed by $A$, and only then reaches the completion-entry row $E$.

The universal-property and comparison rows bind the extension. The row $U$ records the extension-and-uniqueness ledger, while $S$ keeps target comparison inside the displayed separated surface rather than in host equality or a quotient-completion principle.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier has no coordinate for selected representatives, choice, ambient completeness, host function equality, or a detached extension principle, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[MetricCompletionFunctoriality composition]
\label{thm:metric-completion-functoriality-composition}
Let
$$
F=(X,Y,G,A,E,U,S,H,C,P,N)
$$
and
$$
F'=(Y,Z,G',A',E',U',S',H',C',P',N')
$$
be accepted $\MetricCompletionFunctorialityUp$ carriers whose middle metric row $Y$ and completion-entry row compare by the displayed $\hsame$ transport. The composed completion read is the finite replay obtained by first consuming $G,A,E,U,S$ and then consuming $G',A',E',U',S'$. It is sourced by the same $\CauchyCompletionFunctorialityUp$ and $\MetricCompletionUp$ rows named in $P$ and $P'$, and it exports no host-level function composition, quotient-completion equality, selected limit representative, countable choice, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the two carriers. The first packet exposes the route from $X$ to $Y$ through its finite graph, Cauchy-control ledger, completion-entry row, universal-property row, and separated comparison row; the second exposes the same kind of route from $Y$ to $Z$.

Use the displayed $\hsame$ transport on the shared middle rows. This identifies the target metric and completion-entry read of the first packet with the source metric and completion-entry read of the second packet only through the finite transport rows already present in $H$ and $H'$.

Replay the two continuation rows in order. The composed route consumes $C$ and then $C'$, so every source completion read still passes through $\StreamNameUp$, $\RegSeqRatUp$, $\MetricCompletionUp$, $\CompletionUniversalPropertyUp$, and separated comparison rows before the final local name is available.

The nonescape boundary is inherited from the carrier inventory. Neither packet contains host function equality, quotient-completion equality, selected representatives, countable choice, or ambient completeness, and sequential replay of displayed rows cannot create such a coordinate.
\end{proof}

\falsifiablePrediction{Any accepted $\MetricCompletionFunctorialityUp$ consumer that maps a source completion name to a target completion name without displaying the finite graph row, Cauchy-control ledger, completion-entry row, universal-property row, and separated comparison row refutes the carrier surface.}

\independenceWitness{metriccompletion, cauchycompletionfunctor, completionuniversalproperty, dense-isometry-extension, regseqrat, streamname: these sibling chapters supply completion entries, functorial Cauchy routes, universal extension ledgers, dense separated comparison, regular readbacks, and finite windows separately, while this packet binds them into one functorial carrier $F=(X,Y,G,A,E,U,S,H,C,P,N)$.}

\closureat{MetricCompletionFunctorialityUp}{seedStr}

\begin{closurestatus}{\MetricCompletionFunctorialityUp}
  \constructivestory{A $\MetricCompletionFunctorialityUp$ packet is generated from source and target metric rows, a finite map graph, a Cauchy-control ledger, a completion-entry row, a universal-property row, a separated comparison row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-functoriality-carrier}, \autoref{thm:metric-completion-functoriality-namecert-obligations}, and \autoref{thm:metric-completion-functoriality-composition} seed the finite functoriality surface for metric completion maps.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient-completion equality, selected representatives of Cauchy classes, host function extensionality, countable-choice selection, ambient metric completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Cauchy-control routing, completion-entry exactness, universal-property replay, separated comparison, transport, provenance, and local naming for BEDC.Derived.MetricCompletionFunctorialityUp.}
\end{closurestatus}
