\chapter{A Concrete Naming Certificate for $\NetClusterPointUp$}
\label{ch:concrete-instances-net-cluster-point-namecert}
\origin{human}

Following Moore--Smith and Kelley cluster points, the $\NetClusterPointUp$ packet records cluster-point evidence for a directed net through displayed cofinal tails and neighbourhood hits rather than through a selected subnet or an ambient compactness theorem. It sits over the Moore--Smith net carrier of \autoref{ch:concrete-instances-moore-smith-net-namecert}, the directed-index surface of \autoref{ch:concrete-instances-directedset-namecert}, the cofinal subnet route of \autoref{ch:concrete-instances-directedsubnet-namecert}, the convergence interface of \autoref{ch:concrete-instances-netconvergence-namecert}, and the compactness handoff of \autoref{ch:concrete-instances-limit-point-compact-namecert}. The chapter names the finite BEDC landing for cluster-point evidence consumed by later net and compactness arguments, not a quotient of nets, a choice-selected subnet, or a host-level limit principle.

\begin{definition}[Net cluster-point carrier]\label{def:net-cluster-point-carrier}
A $\NetClusterPointUp$ carrier is a finite $\BHist$ packet
$$
K=(M,D,S,T,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MooreSmithNetUp$ source row, naming the directed net, its displayed value windows, and the finite tail ledger consumed by every cluster-point read.
\item $D$ is the $\DirectedSetUp$ index row, exposing the upper-window witnesses needed to compare tail requests.
\item $S$ is the $\DirectedSubnetUp$ cofinal-tail row. It records the cofinal reindexing evidence through which a cluster-point consumer may follow a subnet-shaped tail without selecting an external subnet representative.
\item $T$ is the $\NetConvergenceUp$ neighbourhood-hit row. It records that each displayed neighbourhood request is met along the cofinal tail route before a convergence-facing consumer is exposed.
\item $L$ is the $\LimitPointCompactUp$ handoff row, available only after the Moore--Smith source, directed index, cofinal-tail, and neighbourhood-hit rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the Moore--Smith net row, directed-index row, cofinal-tail row, neighbourhood-hit row, compactness handoff, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a cluster-point request through $M,D,S,T,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\NetClusterPointUp$, $\MooreSmithNetUp$, $\DirectedSetUp$, $\DirectedSubnetUp$, $\NetConvergenceUp$, $\LimitPointCompactUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NetClusterPointUp}$ row.
\end{enumerate}
The carrier contains no quotient-net coordinate, no selected cluster point, no countable-choice subnet selector, no host neighbourhood filter, and no ambient compactness or completeness theorem.
\end{definition}

\begin{theorem}[Net cluster-point NameCert obligations]\label{thm:net-cluster-point-namecert-obligations}
For every accepted $\NetClusterPointUp$ carrier $K=(M,D,S,T,L,H,C,P,N)$, the local $\NameCert_{\NetClusterPointUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed Moore--Smith source, directed-index row, cofinal-tail row, neighbourhood-hit row, compactness handoff, transport, replay, provenance, and local naming rows;
\item source-tail exposure, requiring each cluster-point request to read the $\MooreSmithNetUp$ value window and $\DirectedSetUp$ upper-window witnesses before any neighbourhood-hit row is consumed;
\item cofinal-tail exactness, requiring the $\DirectedSubnetUp$ row $S$ to expose only displayed cofinal reindexing data from the same directed source;
\item neighbourhood-hit routing, requiring $T$ to route every cluster-point neighbourhood request through the $\NetConvergenceUp$ interface before the compactness handoff is visible;
\item compactness handoff, requiring $L$ to consume only the displayed cluster route supplied by $M,D,S,T$ before any $\LimitPointCompactUp$ consumer receives the packet;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$.
\end{enumerate}
Consequently the packet supplies finite Moore--Smith cluster-point evidence and exports no quotient of nets, selected subnet, host neighbourhood filter, countable choice, or ambient compactness theorem.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:net-cluster-point-carrier}. Its analytic rows are $M,D,S,T,L$, and its structural rows are $H,C,P,N$.

The source-tail exposure is read from $M$ and $D$. A cluster-point consumer first names the displayed Moore--Smith net window, then reads the directed upper-window witness that places the request inside the finite tail ledger.

The cofinal route is fixed by $S$. Since $S$ is a $\DirectedSubnetUp$ row over the same directed source, it contributes only displayed cofinal-tail evidence and cannot introduce a selected subnet representative or a countable-choice selector.

The neighbourhood-hit row $T$ is downstream of that cofinal route. It uses the $\NetConvergenceUp$ interface to expose only the finite neighbourhood hits visible along the displayed tail, so no host neighbourhood filter or quotient-net equality is available.

Finally $L$ hands the route to $\LimitPointCompactUp$, while $H,C,P,N$ transport, replay, source, and name the same finite packet. The carrier inventory has no stronger compactness or completeness coordinate, so the local certificate is exhausted by the stated obligations.
\end{proof}

\closureat{NetClusterPointUp}{seedStr}

\begin{closurestatus}{\NetClusterPointUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:net-cluster-point-carrier} and \autoref{thm:net-cluster-point-namecert-obligations} seed the finite cluster-point route through MooreSmithNet, DirectedSet, DirectedSubnet, NetConvergence, LimitPointCompact, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient nets, selected subnets, countable-choice selectors, host neighbourhood filters, ambient compactness, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-tail exposure, cofinal-tail exactness, neighbourhood-hit routing, compactness handoff, transport, replay, provenance, and local naming for BEDC.Derived.NetClusterPointUp.}
  \constructivestory{A $\NetClusterPointUp$ packet is generated from a MooreSmithNet source row, a DirectedSet index row, a DirectedSubnet cofinal-tail row, a NetConvergence neighbourhood-hit row, a LimitPointCompact handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
