\chapter{A Concrete Naming Certificate for $\CauchyCompleteOrderedFieldUniquenessUp$}
\label{ch:concrete-instances-cauchy-complete-ordered-field-uniqueness-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CauchyCompleteOrderedFieldUniquenessUp$ packet names the finite comparison surface between two displayed Cauchy-complete ordered-field presentations of a Real-style object. It reads the terminal $\RealUp$ seal, regular rational sequence rows, dyadic arithmetic ledger, algebra-order rows, the $\CauchyCompleteOrderedFieldUp$ interface, and the $\CompleteArchimedeanFieldUp$ capstone as input packets, then records only the BEDC route that compares their NameCert-visible rows. The chapter exports uniqueness as rowwise route agreement, not as quotient field equality, trichotomy, a selected limit, or a host complete ordered field.

\begin{definition}[Cauchy-complete ordered-field uniqueness carrier]
\label{def:cauchy-complete-ordered-field-uniqueness-carrier}
A $\CauchyCompleteOrderedFieldUniquenessUp$ carrier is a finite $\BHist$ packet
$$
U=(K_0,K_1,R_0,R_1,Q_0,Q_1,D,A_0,A_1,F_0,F_1,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K_0$ and $K_1$ are two accepted $\CauchyCompleteOrderedFieldUp$ packets whose Real-facing reads are to be compared.
\item $R_0$ and $R_1$ are the terminal $\RealUp$ seal rows exposed by $K_0$ and $K_1$.
\item $Q_0$ and $Q_1$ are the $\RegSeqRatUp$ readback rows used before the terminal Real seals are consumed.
\item $D$ is the shared $\DyadicRatCoreUp$ comparison ledger for precision scales, rational windows, and tolerance transfer.
\item $A_0$ and $A_1$ are the $\RealAlgOrderUp$ operation-and-order rows displayed by the two packets.
\item $F_0$ and $F_1$ are the $\CompleteArchimedeanFieldUp$ capstone rows reached from the two Cauchy-complete ordered-field presentations.
\item $G$ is the BEDC comparison route, recording componentwise agreement of the regular-rational windows, dyadic tolerances, Real seals, algebra-order rows, Cauchy-complete ordered-field rows, and complete Archimedean capstone rows.
\item $H$ records componentwise $\hsame$ transport for all displayed rows of $U$.
\item $C$ records displayed $\Cont$ replay from a comparison request through $Q_0,Q_1,D,R_0,R_1,A_0,A_1,K_0,K_1,F_0,F_1,G,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompleteOrderedFieldUniquenessUp$, $\RealUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealAlgOrderUp$, $\CauchyCompleteOrderedFieldUp$, $\CompleteArchimedeanFieldUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompleteOrderedFieldUniquenessUp}$ row.
\end{enumerate}
The classifier compares accepted uniqueness packets only through these rows. It has no coordinate for quotient field equality, trichotomy, a selected limit, a chosen isomorphism outside $G$, or an ambient host complete ordered field.
\end{definition}

\begin{theorem}[Cauchy-complete ordered-field uniqueness NameCert obligations]
\label{thm:cauchy-complete-ordered-field-uniqueness-namecert-obligations}
For every accepted $\CauchyCompleteOrderedFieldUniquenessUp$ carrier
$$
U=(K_0,K_1,R_0,R_1,Q_0,Q_1,D,A_0,A_1,F_0,F_1,G,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompleteOrderedFieldUniquenessUp}$ surface consists exactly of the two displayed $\CauchyCompleteOrderedFieldUp$ packets, their $\RealUp$ seal rows, their $\RegSeqRatUp$ readback rows, the shared $\DyadicRatCoreUp$ comparison ledger, their $\RealAlgOrderUp$ operation-and-order rows, their $\CompleteArchimedeanFieldUp$ capstone rows, the BEDC comparison route $G$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-complete-ordered-field-uniqueness-carrier}. The projection exposes exactly the two Cauchy-complete ordered-field packets, the Real seals, regular-rational readbacks, dyadic comparison ledger, algebra-order rows, complete Archimedean capstone rows, comparison route, transport, replay, provenance, and local naming.

The comparison route first reads $Q_0,Q_1$ against the shared dyadic ledger $D$. This places every tolerance and rational-window comparison before the terminal Real seals $R_0,R_1$ are consumed.

It then compares the ordered-field surfaces through $A_0,A_1$ and the completion-facing surfaces through $K_0,K_1,F_0,F_1$. The row $G$ records exactly this BEDC route and not an external field equality or selected isomorphism.

Finally $H,C,P,N$ preserve, replay, source, and name the same displayed rows. Since quotient field equality, trichotomy, selected limits, and host complete ordered fields have no coordinate in the carrier, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Cauchy-complete ordered-field uniqueness route]
\label{thm:cauchy-complete-ordered-field-uniqueness-route}
Every accepted $\CauchyCompleteOrderedFieldUniquenessUp$ comparison between two displayed Cauchy-complete ordered-field packets factors through
$$
Q_0,Q_1,D \longmapsto R_0,R_1 \longmapsto A_0,A_1,K_0,K_1 \longmapsto F_0,F_1 \longmapsto G,H,C,P,N .
$$
Thus a consumer may cite a finite BEDC route from regular rational readback and dyadic tolerance comparison through Real seals, algebra-order rows, Cauchy-complete ordered-field rows, and complete Archimedean capstone rows. The consumer receives no quotient field equality, trichotomy principle, selected limit, chosen external isomorphism, or host complete ordered field.
\end{theorem}
\begin{proof}
Start with the regular-rational side. The rows $Q_0,Q_1$ are the only readbacks available before Real sealing, and the shared ledger $D$ supplies the dyadic precision and comparison data for both packets.

The route next reaches $R_0,R_1$. Only after these Real seals are displayed may the comparison inspect the algebra-order rows $A_0,A_1$ and the two $\CauchyCompleteOrderedFieldUp$ packets $K_0,K_1$.

The capstone comparison is then made through $F_0,F_1$, the $\CompleteArchimedeanFieldUp$ rows attached to the two presentations. The row $G$ records that the two presentations agree along this displayed BEDC path.

Transport, replay, provenance, and local naming are supplied by $H,C,P,N$. Because no excluded equality, trichotomy, selected-limit, external-isomorphism, or host-field coordinate appears anywhere in the carrier, every uniqueness read factors through the finite route stated above.
\end{proof}

\begin{theorem}[Cauchy-complete ordered-field uniqueness regular-Cauchy dependency]
\label{thm:cauchy-complete-ordered-field-uniqueness-regular-cauchy-dependency}
Every accepted $\CauchyCompleteOrderedFieldUniquenessUp$ packet must route its completion witness through the regular-Cauchy completion surface of \autoref{ch:concrete-instances-regular-cauchy-completion-separated-namecert} and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert} before it compares ordered-field endpoints. The ordered-field comparison therefore reads the displayed completion and real-name rows first; it does not introduce a host complete ordered field, quotient equality, or a selected external isomorphism.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $U$. Its only completion-facing source rows are the regular-rational readbacks $Q_0,Q_1$, the dyadic comparison ledger $D$, the Real seals $R_0,R_1$, and the Cauchy-complete ordered-field rows $K_0,K_1$.

The separated regular-Cauchy completion sibling supplies the finite completion route consumed by those rows, while the Real chapter supplies the terminal seal that the ordered-field comparison is allowed to inspect. Thus the comparison cannot jump directly from $K_0,K_1$ to endpoint equality.

Only after that route is displayed may the algebra-order rows $A_0,A_1$ and capstone rows $F_0,F_1$ be read. The comparison row $G$ records agreement along this finite path, so no host complete ordered field, quotient equality, or external isomorphism is available.
\end{proof}

\falsifiablePrediction{Every $\CauchyCompleteOrderedFieldUniquenessUp$ comparison read factors through two CauchyCompleteOrderedField packets, two Real seals, two RegSeqRat readbacks, one DyadicRatCore comparison ledger, two RealAlgOrder rows, two CompleteArchimedeanField rows, one BEDC comparison route, transport, continuation replay, provenance, and local naming.}

\independenceWitness{real, regseqrat, dyadicratcore, real-alg-order, cauchy-complete-ordered-field, complete-archimedean-field: $\CauchyCompleteOrderedFieldUniquenessUp$ is not bijective to any listed sibling because it jointly carries two displayed complete ordered-field presentations and a rowwise comparison route between them.}

\closureat{CauchyCompleteOrderedFieldUniquenessUp}{seedStr}

\begin{closurestatus}{\CauchyCompleteOrderedFieldUniquenessUp}
  \constructivestory{A $\CauchyCompleteOrderedFieldUniquenessUp$ packet is generated from two CauchyCompleteOrderedField packets, two Real seals, two RegSeqRat readbacks, a DyadicRatCore comparison ledger, two RealAlgOrder rows, two CompleteArchimedeanField rows, one BEDC comparison route, componentwise transport, displayed continuation replay, package provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-complete-ordered-field-uniqueness-carrier}, \autoref{thm:cauchy-complete-ordered-field-uniqueness-namecert-obligations}, and \autoref{thm:cauchy-complete-ordered-field-uniqueness-route} seed the finite comparison surface for two displayed Cauchy-complete ordered-field presentations.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not assert quotient field equality, trichotomy, selected limits, a chosen external isomorphism, a host complete ordered field, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, NameCert obligations, and the rowwise BEDC comparison route for BEDC.Derived.CauchyCompleteOrderedFieldUniquenessUp.}
\end{closurestatus}
