\chapter{A Concrete Naming Certificate for $\AnchorChangeInvariantUp$}
\label{ch:concrete-instances-anchor-change-invariant-namecert}
\origin{ai}

The $\AnchorChangeInvariantUp$ packet realizes the anchor-change invariant surface of \autoref{sec:objectivity-as-invariance} as a finite symmetric transport certificate over observer-history anchors. It sits after the objectivity carrier of \autoref{ch:concrete-instances-reality-constrained-objectivity-namecert}, consumes the anchor-stability packet of \autoref{ch:concrete-instances-anchor-stability-certificate-namecert}, reads the invariant row of \autoref{ch:concrete-instances-interhistinvariant-namecert}, and supplies a focused sibling to the refusal boundary of \autoref{ch:concrete-instances-objectivity-refutation-boundary-namecert}. The carrier is neither a global observer nor a view from nowhere; it is the finite table that records when an invariant survives a reversible change of observer anchor.

\begin{definition}[Anchor-change invariant carrier]
\label{def:anchor-change-invariant-carrier}
An $\AnchorChangeInvariantUp$ carrier is a finite $\BHist$ packet
$$
G=(H,A,I,S,R,L,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $H$ is the finite observer-history family whose anchors are being compared;
\item $A$ is the anchor-change table, with one source anchor, one target anchor, and the displayed reverse row for each admitted comparison;
\item $I$ is the $\InterHistInvariantUp$ row whose value is transported across the anchor change;
\item $S$ is the $\AnchorStabilityCertificateUp$ row certifying that the invariant read is stable under the displayed table;
\item $R$ is the no-privileged-anchor refusal ledger, rejecting routes that factor through one fixed observer anchor;
\item $L$ is the local transport ledger recording the observations, redescription steps, and classifier reads used by the table;
\item $T$ records componentwise $\hsame$ transport and displayed $\Cont$ replay for $H,A,I,S,R,L,P,N$;
\item $P$ is the $\Pkg$ provenance over $\AnchorChangeInvariantUp$, $\RealityConstrainedObjectivityUp$, $\AnchorStabilityCertificateUp$, $\InterHistInvariantUp$, $\RelationalObjectivityUp$, $\ObjectivityRefutationBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AnchorChangeInvariantUp}$ row.
\end{enumerate}
The carrier has no coordinate for a one-way anchor change, privileged observer, hidden synchronizer, anchor-free invariant, quotient of observer histories, or host-side truth value.
\end{definition}

\begin{definition}[Anchor-change invariant classifier]
\label{def:anchor-change-invariant-classifier}
The local $\NameCert_{\AnchorChangeInvariantUp}$ classifier compares accepted carriers only through $H,A,I,S,R,L,T,P,N$. Two packets agree when their observer-history families are matched by the displayed transport, their anchor-change tables contain both directional rows for each admitted comparison, their $\InterHistInvariantUp$ values are transported through the same classifier, their $\AnchorStabilityCertificateUp$ rows certify the same route, and their refusal ledgers reject the same privileged-anchor factorizations.
\end{definition}

\begin{theorem}[Anchor-change invariant NameCert obligations]
\label{thm:anchor-change-invariant-namecert-obligations}
For the carrier of \autoref{def:anchor-change-invariant-carrier}, the local $\NameCert_{\AnchorChangeInvariantUp}$ surface consists exactly of carrier admission for $G=(H,A,I,S,R,L,T,P,N)$, classifier comparison through \autoref{def:anchor-change-invariant-classifier}, invariant transport through $I$, anchor-stability certification through $S$, no-privileged-anchor refusal through $R$, ledger exposure through $L$, componentwise transport and replay through $T$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted packet. The rows $H,A,I,S,R,L$ display the observer family, reversible anchor-change table, invariant value, stability certificate, refusal ledger, and route ledger.

Apply the classifier definition. It compares only the displayed rows and requires both directions of each anchor-change entry before the invariant row may be read as transported content.

The structural rows $T,P,N$ preserve that finite surface by componentwise transport, replay, provenance, and local naming. Since the carrier lists no hidden synchronizer or privileged anchor, the stated rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Anchor-change invariant no privileged anchor]
\label{thm:anchor-change-invariant-no-privileged-anchor}
An accepted $\AnchorChangeInvariantUp$ packet cannot export an invariant route that factors through one fixed observer anchor without the reverse anchor-change row. Such a route is rejected by the refusal ledger $R$ and cannot be read as objective transport.
\end{theorem}
\begin{proof}
Read the anchor-change table $A$ and refusal ledger $R$ from the carrier. Admission requires the displayed reverse row for each comparison and records the rejection of fixed-anchor factorizations.

The classifier of \autoref{def:anchor-change-invariant-classifier} then compares invariant transport only through tables carrying both directions. A one-anchor route lacks the reverse row and is therefore not an accepted comparison.

Consequently the packet may still record local observational content, but it cannot export the invariant as objective anchor-change transport.
\end{proof}

\begin{theorem}[Anchor-change invariant anchor-symmetry totality]
\label{thm:anchor-change-invariant-anchor-symmetry-totality}
Every admitted $\AnchorChangeInvariantUp$ invariant read exposes the source-to-target and target-to-source anchor-change rows in the same finite packet before the read reaches any $\RealityConstrainedObjectivityUp$ or $\RelationalObjectivityUp$ consumer.
\end{theorem}
\begin{proof}
Use the carrier admission row $A$. Its table stores both directional rows for each admitted observer-anchor comparison.

The stability row $S$ and invariant row $I$ are read only after that table is visible. The transport row $T$ replays the same displayed comparison, so downstream objectivity consumers receive the invariant together with the symmetric anchor-change evidence.

No additional route can be supplied by a consumer because $R,L,P,N$ keep the refusal ledger, local route ledger, provenance, and naming rows inside the same packet.
\end{proof}

\falsifiablePrediction{If an invariant route factors through one fixed anchor without a reverse anchor-change row, the AnchorChangeInvariant carrier rejects it as non-objective transport.}

\independenceWitness{realityconstrainedobjectivity, anchorstabilitycertificate, interhistinvariant, relationalobjectivity, objectivityrefutationboundary: these siblings provide objectivity, anchor stability, invariant, relational-objectivity, and refutation surfaces, but none combines a symmetric anchor-change classifier with a no-privileged-anchor refusal ledger.}

The Lean follow-up must provide \texttt{Nontrivial AnchorChangeInvariantUp} and \texttt{FieldFaithful AnchorChangeInvariantUp} in \texttt{lean4/BEDC/Derived/AnchorChangeInvariantUp/TasteGate.lean}.

\closureat{AnchorChangeInvariantUp}{seedStr}

\begin{closurestatus}{\AnchorChangeInvariantUp}
  \constructivestory{An $\AnchorChangeInvariantUp$ packet is generated from a finite observer-history family, reversible anchor-change table, transported invariant row, anchor-stability certificate, no-privileged-anchor refusal ledger, local transport ledger, provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:anchor-change-invariant-carrier}, \autoref{def:anchor-change-invariant-classifier}, \autoref{thm:anchor-change-invariant-namecert-obligations}, \autoref{thm:anchor-change-invariant-no-privileged-anchor}, and \autoref{thm:anchor-change-invariant-anchor-symmetry-totality} bind the finite carrier, classifier, local NameCert obligations, no-privileged-anchor refusal, and anchor-symmetry totality surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not assert global observers, view-from-nowhere semantics, hidden anchor privilege, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires the anchor-change carrier, classifier, invariant-transport, anchor-stability, refusal-ledger, route-ledger, and non-escape obligations to be made explicit.}
\end{closurestatus}
