\chapter{A Concrete Naming Certificate for $\DyadicStepApproximationUp$}
\label{ch:concrete-instances-dyadic-step-approximation-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DyadicStepApproximationUp$ packet records the finite step approximation of a located real interval by dyadic cells, displayed sample values, and an oscillation ledger. It sits after the dyadic rational carrier of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the located interval source of \autoref{ch:concrete-instances-located-real-interval-namecert}, the tagged finite-sum boundary of \autoref{ch:concrete-instances-riemannsum-namecert}, the upper/lower sum surface of \autoref{ch:concrete-instances-darboux-sum-namecert}, and the regulated integration consumer of \autoref{ch:concrete-instances-regulatedintegral-namecert}. The packet gives L10 Real and Completion routes one reusable finite approximation carrier before any quotient of functions, selected mesh limit, open-cover compactness, countable choice, or ambient $\RealUp$ completeness principle is available.

\begin{definition}[Dyadic step approximation carrier]
\label{def:dyadic-step-approximation-carrier}
A $\DyadicStepApproximationUp$ carrier is a finite $\BHist$ packet
$$
A=(I,M,L,V,O,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the located interval source row, read through the endpoint-plus-radius surface of \autoref{ch:concrete-instances-located-real-interval-namecert}.
\item $M$ is the dyadic mesh row from $\DyadicRatCoreUp$. It records the common exponent scale, ordered dyadic breakpoints, adjacent cell widths, endpoint containment, and common-scale distance windows for the interval cells.
\item $L$ is the finite cell ledger. It lists the carried cells of $M$, their inclusion in $I$, the boundary orientation rows, and the adjacency data consumed by Riemann and Darboux readers.
\item $V$ is the step value row. For each carried cell it displays one value row and the finite readback route by which that value is available to $\RiemannSumUp$ and $\DarbouxSumUp$ consumers.
\item $O$ is the oscillation bound row. It records the displayed upper-minus-lower tolerance on each carried cell, using dyadic endpoint and radius comparisons from $M$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the located source, dyadic mesh, cell ledger, step values, and oscillation bounds have been displayed.
\item $H$ records componentwise $\hsame$ transport for $I,M,L,V,O,E$ and for the replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an interval request through the dyadic mesh, finite cells, step values, oscillation bounds, terminal seal, transports, provenance, and local name.
\item $P$ is the $\Pkg$ provenance over $\DyadicStepApproximationUp$, $\LocatedRealIntervalUp$, $\DyadicRatCoreUp$, $\RiemannSumUp$, $\DarbouxSumUp$, $\RegulatedIntegralUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicStepApproximationUp}$ row.
\end{enumerate}
The carrier predicate asserts that these rows form one finite step-approximation surface. It contains no quotient function equality, selected tag family outside $L$, limiting mesh process, open-cover compactness witness, countable-choice schedule, ambient $\RealUp$ completeness theorem, Lean verification, or bridge credential.
\end{definition}
\leanchecked{BEDC.Derived.DyadicStepApproximationUp.DyadicStepApproximationTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Dyadic step approximation obligation surface]
\label{thm:dyadic-step-approximation-obligation-surface}
For every accepted $\DyadicStepApproximationUp$ carrier $A=(I,M,L,V,O,E,H,C,P,N)$, the local $\NameCert_{\DyadicStepApproximationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the located interval source, dyadic mesh, finite cell ledger, step value rows, oscillation bound rows, terminal real seal, transport, replay, provenance, and local naming rows;
\item mesh exactness, requiring every carried breakpoint, width, and endpoint comparison to pass through the common-scale $\DyadicRatCoreUp$ row $M$;
\item interval coverage, requiring every cell in $L$ to lie in the located interval source $I$ through displayed endpoint and radius rows;
\item step-value readback, requiring every value row in $V$ to be read through the same finite cells before a $\RiemannSumUp$ or $\DarbouxSumUp$ consumer can use it;
\item oscillation control, requiring $O$ to compare the upper and lower cell values through the displayed dyadic distance-window ledger;
\item real-seal handoff, requiring the terminal $\RealUp$ row $E$ to be exposed only after $I,M,L,V,O$ are displayed;
\item transport and replay stability, requiring $H$ and $C$ to preserve the same finite rows componentwise;
\item ledger non-escape, excluding quotient function equality, selected mesh limits, arbitrary tag choice, open-cover compactness, countable choice, ambient $\RealUp$ completeness, Lean verification, and bridge checking.
\end{enumerate}
No step-approximation obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-step-approximation-carrier}. The analytic rows are precisely the located interval source $I$, dyadic mesh row $M$, finite cell ledger $L$, step value row $V$, oscillation bound row $O$, and terminal real seal $E$.

Mesh exactness is read from $M$. The dyadic source \autoref{ch:concrete-instances-dyadicratcore-namecert} supplies the common exponent scale, breakpoint comparisons, distance-window rows, and radius ledgers used by every cell of the packet.

Interval coverage is read from $I$ and $L$. The located interval chapter supplies the endpoint-plus-radius boundary, while the ledger lists exactly the cells whose endpoints are certified to lie inside that boundary.

Step-value readback and oscillation control are then finite. The row $V$ gives one displayed value route for each carried cell, and $O$ compares the upper and lower values on that same cell through the dyadic distance-window ledger. These are the rows consumed by the Riemann and Darboux sibling chapters.

Finally, the Real-facing route exposes $E$ only after $I,M,L,V,O$ are visible. The transport row $H$, continuation row $C$, provenance row $P$, and local name $N$ repack the same finite surface. Since the carrier has no quotient-function coordinate, limiting mesh coordinate, arbitrary tag selector, compactness row, choice row, ambient completeness theorem, Lean verification row, or bridge credential, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Dyadic step approximation integration handoff]
\label{thm:dyadic-step-approximation-integration-handoff}
Every $\RiemannSumUp$, $\DarbouxSumUp$, or $\RegulatedIntegralUp$ consumer of an accepted $\DyadicStepApproximationUp$ carrier receives the finite route
$$
I,M,L,V,O \longmapsto E \longmapsto H,C,P,N .
$$
The Riemann consumer reads the displayed cells and values as a tagged finite-sum boundary, the Darboux consumer reads the same cells and oscillation rows as upper/lower finite sums, and the regulated-integral consumer reads the packet as a step approximation ledger before any terminal $\RealUp$ seal is consumed.
\end{theorem}
\begin{proof}
Start from the obligation surface of \autoref{thm:dyadic-step-approximation-obligation-surface}. It confines every accepted packet to the located source, dyadic mesh, finite cell ledger, value rows, oscillation rows, terminal seal, and structural rows.

For a Riemann consumer, apply the sibling surface of \autoref{ch:concrete-instances-riemannsum-namecert}. The cell ledger $L$ supplies the carried mesh cells and the row $V$ supplies the finite value reads, so the consumer obtains a tagged finite-sum boundary rather than a hidden tag family.

For a Darboux consumer, apply \autoref{ch:concrete-instances-darboux-sum-namecert}. The same cells and value rows are read through $O$ as upper/lower oscillation data, so the upper-minus-lower comparison remains a displayed finite ledger.

For a regulated-integral consumer, apply \autoref{ch:concrete-instances-regulatedintegral-namecert}. The packet is consumed as a step approximation ledger before the $\RealUp$ seal $E$ is public. Thus all three consumers receive the same finite route, and the excluded quotient, limit, compactness, choice, and ambient-completeness objects have no row through which to enter.
\end{proof}

\closureat{DyadicStepApproximationUp}{seedStr}

\begin{closurestatus}{\DyadicStepApproximationUp}
  \constructivestory{A $\DyadicStepApproximationUp$ packet is generated from a located interval source, a $\DyadicRatCoreUp$ mesh row, a finite cell ledger, step value rows, oscillation bound rows, a terminal $\RealUp$ seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-step-approximation-carrier}, \autoref{thm:dyadic-step-approximation-obligation-surface}, and \autoref{thm:dyadic-step-approximation-integration-handoff} seed the finite step-approximation carrier consumed by RiemannSum, DarbouxSum, and RegulatedIntegral routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient function equality, selected mesh limits, arbitrary tag choice, open-cover compactness, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, mesh exactness, interval coverage, step-value readback, oscillation control, real-seal handoff, transport stability, replay stability, provenance exhaustion, and integration handoff for BEDC.Derived.DyadicStepApproximationUp.}
\end{closurestatus}
