\chapter{A Concrete Naming Certificate for $\SecantMethodUp$}
\label{ch:concrete-instances-secant-method-namecert}
\origin{human}

Following Traub and Ortega--Rheinboldt on iterative root-finding, the $\SecantMethodUp$ packet records the finite two-point root-finding surface used by the L10 completion-facing numerical-analysis route. It sits beside the Newton--Kantorovich packet of \autoref{ch:concrete-instances-newton-kantorovich-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window interface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only the displayed bracketing windows, two previous iterates, finite secant denominator checks, residual reads, next-iterate rows, Cauchy handoff, transport, replay, provenance, and local naming; it does not assert global convergence, a derivative bound, quotient equality of reals, a selected host limit, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Secant method carrier]
\label{def:secant-method-carrier}
A $\SecantMethodUp$ carrier is a finite $\BHist$ packet
$$
S=(F,X,Y,D,R,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the function-evaluation row, naming the finite $\RealUp$ input and residual observations used by the root-finding request.
\item $X$ and $Y$ are the two previous iterate rows, each exposed through $\RegSeqRatUp$ readback and the same $\StreamNameUp$ window schedule.
\item $D$ is the $\DyadicRatCoreUp$ denominator-separation row, recording the finite nonzero secant-denominator comparison needed before the next iterate can be read.
\item $R$ is the residual-control row, binding the two displayed residuals and the candidate next residual to finite dyadic tolerances.
\item $W$ is the $\StreamNameUp$ window row for the iterate, residual, denominator, and tolerance observations.
\item $Q$ is the $\RegSeqRatUp$ handoff row that reads every iterate and residual window as regular rational data.
\item $E$ is the downstream $\RealUp$ seal reached only after $F,X,Y,D,R,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for function-evaluation, iterate, denominator, residual, window, readback, endpoint, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a secant request through $F,X,Y,D,R,W,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\SecantMethodUp$, $\NewtonKantorovichUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SecantMethodUp}$ row.
\end{enumerate}
The classifier accepts the packet only through these finite rows. There is no coordinate for derivative availability, a completed limit point, quotient equality of real presentations, an unbounded convergence search, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Secant method NameCert obligations]
\label{thm:secant-method-namecert-obligations}
For the carrier of \autoref{def:secant-method-carrier}, the local $\NameCert_{\SecantMethodUp}$ surface consists exactly of carrier admission for $S=(F,X,Y,D,R,W,Q,E,H,C,P,N)$, function-evaluation admission through $F$, two-iterate admission through $X,Y$, dyadic denominator-separation admission through $D$, residual-control admission through $R$, finite-window admission through $W$, regular-rational readback through $Q$, downstream $\RealUp$ sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier. The function row $F$ and iterate rows $X,Y$ expose the only data from which the secant step may be read, and both iterate rows are tied to the same finite window surface.

The denominator and residual checks are displayed before the next-iterate read. The row $D$ supplies a dyadic nonzero comparison for the secant denominator, while $R$ records residual tolerances using the same finite observations.

Readback then passes through $W$ and $Q$. The $\StreamNameUp$ row supplies the requested windows, and $\RegSeqRatUp$ turns those windows into regular rational data before the downstream $\RealUp$ seal $E$ is visible.

Finally $H,C,P,N$ transport, replay, source, and name this route. Since the carrier contains no derivative row, limit selector, quotient equality, unbounded search, choice principle, or ambient completeness coordinate, the listed rows exhaust the local obligations.
\end{proof}

\begin{theorem}[Secant method Cauchy handoff]
\label{thm:secant-method-cauchy-handoff}
Every completion-facing read of an accepted $\SecantMethodUp$ packet factors through the finite route
$$
\StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \SecantMethodUp \longmapsto \RealUp .
$$
The handoff first exposes finite iterate and residual windows, then regular rational readback, then dyadic denominator and residual budgets, and only then the terminal real-name seal. It supplies no independent convergence theorem, no derivative-based Newton certificate, no selected limit, and no ambient completeness principle.
\end{theorem}
\begin{proof}
Start with a completion-facing consumer. The carrier forces the request to read $W$ and $Q$ before a secant step can be interpreted, so the iterates and residuals are finite regular rational observations rather than host real representatives.

Next inspect the dyadic rows. The denominator-separation row $D$ and residual-control row $R$ provide the only permitted comparison data for the next iterate, and both are attached to the same displayed windows.

The $\RealUp$ seal $E$ is reached after those rows have been replayed through $C$ and transported through $H$. Thus the exported handoff is a finite Cauchy-facing route, not an assertion of global convergence, derivative control, selected limits, quotient equality, countable choice, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\SecantMethodUp$ completion-facing read factors through finite StreamName windows, RegSeqRat readback, DyadicRatCore denominator and residual budgets, displayed secant-step rows, a downstream RealUp seal, hsame transport, Cont replay, Pkg provenance, and local NameCert evidence.}

\independenceWitness{newtonkantorovich, regseqrat, dyadicratcore, streamname, real: $\SecantMethodUp$ is not bijective to any listed sibling because it jointly carries two previous iterate rows, a finite secant denominator check, residual-control rows, regular rational readback, dyadic tolerance data, a downstream Real seal, transport, replay, provenance, and local naming.}

\closureat{SecantMethodUp}{seedStr}

\begin{closurestatus}{\SecantMethodUp}
  \constructivestory{A $\SecantMethodUp$ packet is generated from function-evaluation rows, two previous iterate rows, dyadic denominator-separation and residual-control rows, finite StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:secant-method-carrier}, \autoref{thm:secant-method-namecert-obligations}, and \autoref{thm:secant-method-cauchy-handoff} seed the finite secant root-finding route from regular rational windows to the Real endpoint seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, global convergence, derivative-control hypotheses, quotient equality of real presentations, selected limits, countable choice, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, two-iterate admission, denominator-separation exactness, residual-control routing, Cauchy handoff, transport, replay, provenance, and local naming for BEDC.Derived.SecantMethodUp.}
\end{closurestatus}
