\chapter{A Concrete Naming Certificate for $\CauchyCompletionComonadUp$}
\label{ch:concrete-instances-cauchy-completion-comonad-namecert}
\origin{human}

Following Mac Lane on comonads and Bishop--Bridges on constructive Cauchy completion, the $\CauchyCompletionComonadUp$ packet records the finite completion-read surface obtained by reading already displayed completion data back through counit and comparison rows. It is paired with the monad packet of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, the Kleisli consumer boundary of \autoref{ch:concrete-instances-cauchy-completion-kleisli-namecert}, the counit packet of \autoref{ch:concrete-instances-cauchy-completion-counit-namecert}, the comparison packet of \autoref{ch:concrete-instances-cauchy-completion-comparison-namecert}, and the triangle-identity packet of \autoref{ch:concrete-instances-cauchy-completion-triangle-identity-namecert}. The analytic route is the same finite L10 exit through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}; the chapter names this dual read as finite NameCert data rather than as a quotient completion object.

\begin{definition}[CauchyCompletionComonad carrier]
\label{def:cauchy-completion-comonad-carrier}
A $\CauchyCompletionComonadUp$ carrier is a finite $\BHist$ packet
$$
G=(M,K,E,Q,T,S,R,D,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\CauchyCompletionMonadUp$ route whose source, unit, bind, finite-window, readback, and terminal-seal rows are being read in the opposite direction.
\item $K$ is the $\CauchyCompletionKleisliUp$ consumer row, displaying how a completion-facing request reaches the same finite source and seal rows.
\item $E$ is the $\CauchyCompletionCounitUp$ return row from displayed completion data to the real-facing boundary.
\item $Q$ is the $\CauchyCompletionComparisonUp$ row comparing the monad-facing and counit-facing reads over the same finite completion route.
\item $T$ is the $\CauchyCompletionTriangleIdentityUp$ row identifying the two displayed unit-counit composites with the direct completion read.
\item $S$ is the $\StreamNameUp$ finite-window row inspected before any rational readback or terminal seal is exposed.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row consumed by the completion read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and observation ledger attached to the same finite windows.
\item $A$ is the terminal $\RealUp$ seal reached only after $S,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $M,K,E,Q,T,S,R,D,A$ and the structural rows.
\item $C$ records displayed $\Cont$ replay for consumers that inspect the comultiplication side, the counit side, the comparison side, or the terminal real-facing route.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionComonadUp$, $\CauchyCompletionMonadUp$, $\CauchyCompletionKleisliUp$, $\CauchyCompletionCounitUp$, $\CauchyCompletionComparisonUp$, $\CauchyCompletionTriangleIdentityUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionComonadUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient-completion equality, selected Cauchy representatives, host equality of completed objects, countable choice, ambient completeness, $\RealUp$ completeness, or bridge-axis evidence.
\end{definition}

\begin{theorem}[CauchyCompletionComonad NameCert obligations]
\label{thm:cauchy-completion-comonad-namecert-obligations}
For every accepted $\CauchyCompletionComonadUp$ carrier $G=(M,K,E,Q,T,S,R,D,A,H,C,P,N)$, the local $\NameCert_{\CauchyCompletionComonadUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the monad, Kleisli, counit, comparison, triangle, finite-window, regular-readback, dyadic-ledger, terminal-seal, transport, replay, provenance, and local naming rows;
\item comultiplication exposure, requiring every doubled completion-read request to pass through $M,K,Q,T$ before a terminal seal can be inspected;
\item counit return, requiring every already displayed completion read to pass through $E$ before it reaches $S,R,D,A$;
\item finite triangle compatibility, requiring the comultiplication-counit composites to reach the same displayed $S,R,D,A$ route as the direct completion read;
\item classifier stability, requiring transported packets with the same displayed rows to be compared only by the carried $\hsame$ and $\Cont$ data;
\item non-escape, requiring $P,N$ to source and name no quotient completion, selected representative, countable-choice schedule, host equality, ambient completeness theorem, $\RealUp$ completeness theorem, Lean verification credential, or bridge credential.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-comonad-carrier}. The tuple lists the monad, Kleisli, counit, comparison, triangle, finite-window, regular-readback, dyadic-ledger, terminal-seal, transport, replay, provenance, and local naming rows.

Comultiplication exposure is read from $M,K,Q,T$. The monad and Kleisli rows give the doubled completion consumer surface, the comparison row aligns it with the already displayed completion read, and the triangle row identifies the visible composites with the direct route.

Counit return is read from $E$. Once completion data have already been displayed, the packet forces their return through $S,R,D,A$ before any real-facing consumer sees a terminal seal.

The structural obligations are componentwise. The rows $H$ and $C$ preserve and replay only the displayed packet, while $P$ and $N$ source and name that packet. Since no excluded coordinate occurs in the carrier, no stronger completion object can be exported.
\end{proof}

\begin{theorem}[CauchyCompletionComonad comultiplication and counit route]
\label{thm:cauchy-completion-comonad-comultiplication-counit-route}
Let $G=(M,K,E,Q,T,S,R,D,A,H,C,P,N)$ be an accepted $\CauchyCompletionComonadUp$ carrier. Every consumer of the finite comultiplication-counit surface factors through the displayed route
$$
M,K \longmapsto Q,T \longmapsto E \longmapsto S,R,D \longmapsto A \longmapsto H,C,P,N .
$$
The route exposes a completion read only after the monad-facing and Kleisli-facing rows have been compared with the counit-facing return and then passed through the finite $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows. It exports no quotient completion, selected representative, host equality of completed objects, countable-choice selector, ambient completeness theorem, or bridge credential.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only doubled completion-read rows are $M$ and $K$, so a comultiplication-facing request first reads the monad route and the Kleisli consumer boundary.

The middle comparison is forced by $Q$ and $T$. The comparison row aligns the monad-facing read with the counit-facing return, and the triangle row identifies the two visible composites with the same direct completion route.

The counit row $E$ then returns the displayed completion read to the terminal finite route. That route must pass through the finite window $S$, the regular readback $R$, the dyadic ledger $D$, and the real seal $A$.

Finally $H,C,P,N$ transport, replay, source, and name the same rows. Since the carrier contains no coordinate for quotient completions, selected representatives, host equality, countable choice, ambient completeness, or bridge evidence, the displayed route is the whole comonad surface.
\end{proof}

\begin{theorem}[CauchyCompletionComonad finite completion-read boundary]
\label{thm:cauchy-completion-comonad-finite-read-boundary}
Every completion-facing, $\StreamNameUp$-facing, $\RegSeqRatUp$-facing, $\DyadicRatCoreUp$-facing, or $\RealUp$-facing read exported by an accepted $\CauchyCompletionComonadUp$ carrier is generated by the rows of \autoref{def:cauchy-completion-comonad-carrier}. In particular, the packet gives later completion algebra and reflector consumers a finite non-quotient read surface, not an ambient completed object.
\end{theorem}
\begin{proof}
Read the completion-facing side first. The only completion control rows are $M,K,E,Q,T$, so every completion-facing consumer must factor through the monad route, Kleisli route, counit return, comparison row, and triangle row.

Read the analytic side next. The only finite observation and terminal seal rows are $S,R,D,A$, so every $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ consumer reaches the terminal read through those rows.

The structural rows $H,C,P,N$ preserve the same surface and add no new carrier coordinate. Therefore algebra and reflector consumers can reuse the finite read boundary, but they cannot obtain a quotient completion, selected limit, host completed object, ambient completeness theorem, or bridge credential from it.
\end{proof}

\closureat{CauchyCompletionComonadUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionComonadUp}
  \constructivestory{A $\CauchyCompletionComonadUp$ packet is generated from CauchyCompletionMonad, CauchyCompletionKleisli, CauchyCompletionCounit, CauchyCompletionComparison, CauchyCompletionTriangleIdentity, StreamName, RegSeqRat, DyadicRatCore, Real, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-comonad-carrier}, \autoref{thm:cauchy-completion-comonad-namecert-obligations}, \autoref{thm:cauchy-completion-comonad-comultiplication-counit-route}, and \autoref{thm:cauchy-completion-comonad-finite-read-boundary} seed the finite dual completion-read surface over the L10 Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient-completion equality, selected Cauchy representatives, host equality of completed objects, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, comultiplication exposure, counit return, triangle compatibility, classifier stability, non-escape, and a Lean carrier/obligation formalization for BEDC.Derived.CauchyCompletionComonadUp.}
\end{closurestatus}
