\chapter{A Concrete Naming Certificate for $\TriggerBlockerDualityUp$}
\label{ch:concrete-instances-trigger-blocker-duality-namecert}
\origin{ai}

The $\TriggerBlockerDualityUp$ packet realizes the blocker-complex reading of \autoref{def:philosophy-blocker-complex}, \autoref{thm:philosophy-maximal-blockers}, \autoref{thm:philosophy-blocker-intersections}, and \autoref{thm:philosophy-blocker-nerve} as finite BEDC NameCert data. It consumes the six-boundary coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the finite support algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}, the Boolean trigger lattice of \autoref{ch:concrete-instances-boolean-trigger-lattice-namecert}, the Alexander-dual trigger algebra of \autoref{ch:concrete-instances-alexander-dual-trigger-algebra-namecert}, and the DNA boundary-tile source of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}. The packet names trigger-blocker duality by finite blocker-complex, maximal-blocker, intersection, nerve, transport, provenance, and local NameCert rows; it is not a biological stochastic model, a hidden codon semantics, an unbounded trigger search, or an external homology oracle.

\begin{definition}[Trigger-blocker duality carrier]
\label{def:trigger-blocker-duality-carrier}
A $\TriggerBlockerDualityUp$ carrier is a finite $\BHist$ packet
$$
D=(S,A,L,B,I,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SixBoundaryTileCoverageUp$ row exposing the finite boundary-trigger coordinates and coverage ranks.
\item $A$ is the $\WindowCoverageTriggerAlgebraUp$ row carrying the finite trigger-support closure and blocker threshold data.
\item $L$ is the $\BooleanTriggerLatticeUp$ row recording meet, join, rank, and observed trigger-table reads.
\item $B$ is the blocker-complex row, displaying the four maximal blockers obtained by omitting one trigger coordinate and the non-trigger face predicate of \autoref{def:philosophy-blocker-complex}.
\item $I$ is the intersection row, recording the sizes $14,6,2,0$ for one-, two-, three-, and four-fold omitted-coordinate intersections.
\item $V$ is the nerve row, recording the four vertices, six edges, four triangular faces, and absent three-simplex of the blocker nerve.
\item $H$ records componentwise $\hsame$ transport for $S,A,L,B,I,V$ and for the continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from trigger coverage through blocker readback and nerve readback.
\item $P$ is the $\Pkg$ provenance over $\TriggerBlockerDualityUp$, $\SixBoundaryTileCoverageUp$, $\WindowCoverageTriggerAlgebraUp$, $\BooleanTriggerLatticeUp$, $\AlexanderDualTriggerAlgebraUp$, $\DnaWindowSixBoundaryTileUp$, the source blocker-complex vision, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\TriggerBlockerDualityUp}$ row.
\end{enumerate}
The carrier contains no hidden biological semantics, no stochastic evolutionary model, no quotient codon space, no unbounded trigger enumeration, and no external homology oracle.
\end{definition}

\begin{theorem}[Trigger-blocker duality NameCert obligations]
\label{thm:trigger-blocker-duality-namecert-obligations}
For every accepted $\TriggerBlockerDualityUp$ carrier $D=(S,A,L,B,I,V,H,C,P,N)$, the local $\NameCert_{\TriggerBlockerDualityUp}$ surface consists exactly of carrier admission for the displayed rows, coverage exposure through $S$, trigger-algebra exposure through $A$, Boolean lattice exposure through $L$, blocker-complex exactness through $B$, maximal-blocker intersection accounting through $I$, blocker-nerve readback through $V$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:trigger-blocker-duality-carrier}. The rows $S,A,L$ expose the trigger side, the rows $B,I,V$ expose the blocker and nerve side, and $H,C,P,N$ transport, replay, source, and name the packet.

The trigger side is finite because $S$ displays the boundary-tile coverage coordinates, $A$ displays the support-closure algebra, and $L$ displays Boolean meet, join, and rank rows over the same finite support surface.

The blocker side is finite because $B$ lists the four maximal omitted-coordinate blockers, $I$ records the displayed intersection sizes, and $V$ records the nerve readback. These are exactly the rows needed by \autoref{thm:philosophy-blocker-nerve}.

Transport and replay preserve the same rows componentwise. Since the carrier has no coordinate for hidden biological meaning, stochastic evolution, quotient codon semantics, unbounded search, or an external homology oracle, no accepted NameCert obligation can project one of those objects.
\end{proof}

\begin{theorem}[Trigger-blocker duality finite nerve readback]
\label{thm:trigger-blocker-duality-finite-nerve-readback}
Every accepted $\TriggerBlockerDualityUp$ read of the blocker nerve factors through the finite route
$$
\SixBoundaryTileCoverageUp,\ \WindowCoverageTriggerAlgebraUp,\ \BooleanTriggerLatticeUp,\ \AlexanderDualTriggerAlgebraUp,\ \DnaWindowSixBoundaryTileUp \longmapsto B,I,V,H,C,P,N .
$$
Removing one maximal-blocker row changes the blocker nerve readback because $V$ is computed from the four displayed blocker rows and their intersection ledger $I$.
\end{theorem}
\begin{proof}
Apply the obligation surface of \autoref{thm:trigger-blocker-duality-namecert-obligations}. It forces every accepted nerve read to expose the trigger-side coverage, algebra, and Boolean lattice rows before the blocker rows are available.

The nerve row $V$ is tied to $B$ and $I$. The four vertices are the four maximal-blocker rows, the six edges and four triangular faces are read from the nonempty two- and three-fold intersections, and the absent three-simplex is read from the empty four-fold intersection.

If one maximal-blocker row is removed, the vertex set of $V$ changes and the intersection ledger no longer has the same four omitted-coordinate coordinates. Thus the accepted blocker nerve readback changes before any downstream trigger-spectrum consumer can use the packet.
\end{proof}

\falsifiablePrediction{Removing one displayed maximal-blocker row from an accepted $\TriggerBlockerDualityUp$ carrier changes the blocker nerve readback through $V$ before any downstream trigger-spectrum consumer can preserve the certificate.}

\independenceWitness{six-boundary-tile-coverage, window-coverage-trigger-algebra, boolean-trigger-lattice, alexander-dual-trigger-algebra, dna-window-six-boundary-tile: none is bijective with $\TriggerBlockerDualityUp$ because this packet jointly carries blocker-complex rows, maximal-blocker rows, intersection rows, nerve rows, transport, replay, provenance, and local naming.}

The Lean follow-up for this chapter must provide \texttt{Nontrivial TriggerBlockerDualityUp} and \texttt{FieldFaithful TriggerBlockerDualityUp} instances in \texttt{BEDC.Derived.TriggerBlockerDualityUp} so that $S,A,L,B,I,V,H,C,P,N$ remain separate displayed fields.

\closureat{TriggerBlockerDualityUp}{seedStr}

\begin{closurestatus}{\TriggerBlockerDualityUp}
  \constructivestory{A $\TriggerBlockerDualityUp$ packet is generated from six-boundary coverage rows, trigger-algebra rows, Boolean trigger-lattice rows, blocker-complex rows, maximal-blocker intersection rows, blocker-nerve rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:trigger-blocker-duality-carrier}, \autoref{thm:trigger-blocker-duality-namecert-obligations}, and \autoref{thm:trigger-blocker-duality-finite-nerve-readback} seed the finite blocker-complex, maximal-blocker, intersection, and nerve packet consumed by downstream trigger-spectrum chapters.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological stochastic semantics, quotient codon semantics, unrestricted trigger search, external homology computation, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, coverage exposure, trigger-algebra exposure, Boolean lattice exposure, blocker-complex exactness, intersection accounting, nerve readback, Nontrivial TriggerBlockerDualityUp, and FieldFaithful TriggerBlockerDualityUp for BEDC.Derived.TriggerBlockerDualityUp.}
\end{closurestatus}
