\chapter{A Concrete Naming Certificate for $\GlobalFiberSpectraUp$}
\label{ch:concrete-instances-global-fiber-spectra-namecert}
\origin{ai}

The $\GlobalFiberSpectraUp$ packet realizes the global-fiber spectra branch of \autoref{thm:philosophy-complete-global-fiber-tiles-standard-code} and \autoref{thm:philosophy-standard-code-q-one-edge-spectrum} as finite BEDC NameCert data. It sits beside the six-boundary tile coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the window-coverage trigger algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}, and the greedy spectral closure packet of \autoref{ch:concrete-instances-greedy-spectral-closure-namecert}; those siblings expose coverage, trigger, and closure faces, while this packet records the global tripleton, singleton, edge-spectrum, tile, trigger, transport, replay, provenance, and naming rows together.

\begin{definition}[GlobalFiberSpectra carrier]
\label{def:global-fiber-spectra-carrier}
A $\GlobalFiberSpectraUp$ carrier is a finite $\BHist$ packet
$$
G=(F,T,E,L,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the global codon-cube fiber row recording tripleton, singleton, doubleton, quartet, and sextupleton multiplicities for the standard-code classifier.
\item $T$ is the complete global fiber tile row recording the displayed Ile/Met and Stop/Trp $3+1$ tiles.
\item $E$ is the edge-spectrum row recording same-class and cross-class Hamming edge counts by bit direction.
\item $L$ is the sibling tile-coverage row over $\SixBoundaryTileCoverageUp$ and finite standard-tile enumeration data.
\item $R$ is the trigger handoff row over $\WindowCoverageTriggerAlgebraUp$ and $\GreedySpectralClosureUp$.
\item $H$ is the componentwise $\hsame$ transport row for the fiber, tile, edge, coverage, trigger, replay, provenance, and local naming data.
\item $C$ is the displayed $\Cont$ replay row for standard-code reads.
\item $P$ is the $\Pkg$ provenance over $\GlobalFiberSpectraUp$, $\SixBoundaryTileCoverageUp$, $\WindowCoverageTriggerAlgebraUp$, $\GreedySpectralClosureUp$, finite codon-cube tiles, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\GlobalFiberSpectraUp}$ row.
\end{enumerate}
The carrier has no coordinate for a hidden genetic-code oracle, biochemical causation claim, infinite codon family, non-displayed trigger semantics, or host probability model.
\end{definition}

\begin{theorem}[GlobalFiberSpectra NameCert obligations]
\label{thm:global-fiber-spectra-namecert-obligations}
For every accepted $\GlobalFiberSpectraUp$ carrier $G=(F,T,E,L,R,H,C,P,N)$, the local $\NameCert_{\GlobalFiberSpectraUp}$ surface consists exactly of global fiber multiplicity, complete global fiber tile exposure, edge-spectrum exposure, six-boundary tile coverage, trigger handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. A standard-code read cannot expose trigger interpretation before the global tripleton, singleton, edge-spectrum, tile, and sibling coverage rows have been displayed.
\end{theorem}
\begin{proof}
Project the carrier rows. The fiber row $F$, tile row $T$, and edge row $E$ are the only global-spectrum data available to the packet.

Route sibling dependence through $L$ and $R$. The coverage row keeps the packet tied to six-boundary and standard-tile data, while the trigger handoff row records the window-coverage and greedy-closure interfaces without exposing trigger interpretation early.

Use $H,C,P,N$ to transport, replay, source, and name the same finite route. Since no hidden oracle, biochemical causation coordinate, infinite family, non-displayed trigger semantics, or host probability model is present, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[GlobalFiberSpectra sibling separation]
\label{thm:global-fiber-spectra-sibling-separation}
An accepted $\GlobalFiberSpectraUp$ packet is not determined by any one of $\SixBoundaryTileCoverageUp$, $\WindowCoverageTriggerAlgebraUp$, $\GreedySpectralClosureUp$, or finite standard-tile enumeration alone. The packet jointly carries global fiber multiplicity $F$, complete $3+1$ tile rows $T$, Hamming edge-spectrum rows $E$, sibling coverage $L$, trigger handoff $R$, transport $H$, replay $C$, provenance $P$, and local naming $N$.
\end{theorem}
\begin{proof}
Read each sibling as a proper face. Six-boundary coverage supplies tile coverage, window-coverage trigger algebra supplies trigger handoff, greedy spectral closure supplies closure rows, and standard-tile enumeration supplies finite local tiles.

The global fiber and edge rows are additional coordinates. They record global tripleton, singleton, and direction-sensitive edge spectra before trigger interpretation is exposed.

Therefore no sibling alone is bijective to the packet. The structural rows $H,C,P,N$ preserve the joint route and prevent any one face from replacing the whole $\GlobalFiberSpectraUp$ carrier.
\end{proof}

\falsifiablePrediction{Every accepted $\GlobalFiberSpectraUp$ standard-code read factors through displayed global tripleton, singleton, edge-spectrum, and tile rows before any trigger interpretation is exposed.}

\independenceWitness{sixboundarytilecoverage, windowcoveragetriggeralgebra, greedyspectralclosure, standardtileenumeration: $\GlobalFiberSpectraUp$ is not bijective to these siblings because it jointly carries global fiber multiplicity, local tile spectrum, edge counts, trigger handoff, transport, replay, provenance, and local naming.}

The Lean follow-up in \texttt{lean4/BEDC/Derived/GlobalFiberSpectraUp.lean} must provide explicit $\mathsf{Nontrivial}\ \GlobalFiberSpectraUp$ and $\mathsf{FieldFaithful}\ \GlobalFiberSpectraUp$ TasteGate instances preserving $F,T,E,L,R,H,C,P,N$.

\closureat{GlobalFiberSpectraUp}{seedStr}

\begin{closurestatus}{\GlobalFiberSpectraUp}
  \constructivestory{A $\GlobalFiberSpectraUp$ packet is generated from finite codon-cube fiber rows, complete tile rows, edge-spectrum rows, sibling coverage rows, trigger handoff rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:global-fiber-spectra-carrier}, \autoref{thm:global-fiber-spectra-namecert-obligations}, and \autoref{thm:global-fiber-spectra-sibling-separation} bind the global-fiber spectra vision to finite codon-cube fiber, tile, edge, trigger, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not assert biochemical causation, hidden genetic-code optimality, host probability semantics, non-displayed trigger interpretation, Lean verification, or bridge checking for $\GlobalFiberSpectraUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, global-fiber exposure, edge-spectrum exactness, sibling-separation exactness, Nontrivial and FieldFaithful instances, and trigger nonescape for BEDC.Derived.GlobalFiberSpectraUp.}
\end{closurestatus}
