\chapter{A Concrete Naming Certificate for $\KirszbraunExtensionUp$}
\label{ch:concrete-instances-kirszbraun-extension-namecert}
\origin{human}

Following Kirszbraun and the Banach-space tradition around nonexpansive and Lipschitz extension theorems, the $\KirszbraunExtensionUp$ packet records the finite certificate surface needed to read a Lipschitz map on a metric subspace as a convex inner-product-valued extension request. It sits beside the metric subspace packet of \autoref{ch:concrete-instances-metric-subspace-namecert}, the Lipschitz map packet of \autoref{ch:concrete-instances-lipschitzmap-namecert}, the reusable extension interface of \autoref{ch:concrete-instances-lipschitz-extension-namecert}, the convex target surface of \autoref{ch:concrete-instances-convexset-namecert}, the inner-product target source of \autoref{ch:concrete-instances-innerproduct-namecert}, and the metric source of \autoref{ch:concrete-instances-metric-namecert}. The chapter names the finite Kirszbraun-facing route without claiming Hilbert-space completeness, a host extension operator, pointwise equality of functions, or a selected global formula.

\begin{definition}[Kirszbraun extension carrier]
\label{def:kirszbraun-extension-carrier}
A $\KirszbraunExtensionUp$ carrier is a finite $\BHist$ packet
$$
K=(X,A,L,Y,V,B,F,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the ambient $\MetricUp$ row for the source observations.
\item $A$ is the $\MetricSubspaceUp$ row, including the membership, inclusion, and inherited-distance route from $A$ into $X$.
\item $L$ is the source $\LipschitzMapUp$ row on $A$, carrying the finite graph window and displayed Lipschitz constant.
\item $Y$ is the target $\InnerProductUp$ row, read through its vector, scalar-form, norm-seed, and metric-seed observations.
\item $V$ is the target $\ConvexSetUp$ row inside the inner-product carrier, recording the admitted convex codomain surface for extension values.
\item $B$ is the Lipschitz-constant ledger, recording the rational bound, the source-distance reads through $A,X$, and the target-distance reads through $Y,V$.
\item $F$ is the extension graph row over the ambient metric window $X$ with values admitted by $V$.
\item $R$ is the restriction and bound row, requiring source points admitted by $A$ to replay the graph of $L$ and requiring every displayed ambient pair of $F$ to respect the same ledger $B$.
\item $H$ records componentwise $\hsame$ transport for the ambient metric, subspace, source Lipschitz map, target inner-product, convex codomain, Lipschitz ledger, extension graph, restriction, replay, provenance, and local name rows.
\item $C$ records displayed $\Cont$ replay from a Kirszbraun extension request through $X,A,L,Y,V,B,F,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\KirszbraunExtensionUp$, $\MetricSubspaceUp$, $\LipschitzMapUp$, $\LipschitzExtensionUp$, $\ConvexSetUp$, $\InnerProductUp$, $\MetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\KirszbraunExtensionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers componentwise through these rows. It contains no coordinate for a host Hilbert space, a global extension operator, quotient equality of functions, countable choice, ambient compactness, or unbounded real completion.
\end{definition}

\begin{theorem}[Kirszbraun extension NameCert obligations]
\label{thm:kirszbraun-extension-namecert-obligations}
For every accepted $\KirszbraunExtensionUp$ carrier $K=(X,A,L,Y,V,B,F,R,H,C,P,N)$, the local $\NameCert_{\KirszbraunExtensionUp}$ surface consists exactly of carrier admission for the displayed tuple, metric-subspace inclusion through $A$, source Lipschitz-map admission through $L$, inner-product target admission through $Y$, convex codomain admission through $V$, Lipschitz-constant ledger readback through $B$, extension-graph admission through $F$, restriction and bound exactness through $R$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.

The finite route is
$$
X,A \longmapsto L \longmapsto Y,V \longmapsto B,F,R \longmapsto H,C,P,N .
$$
No obligation is discharged by a host extension formula, a quotient of maps, or a hidden Hilbert-space theorem.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:kirszbraun-extension-carrier}. The displayed rows are exactly $X,A,L,Y,V,B,F,R,H,C,P,N$.

The source side is read through $X,A,L$. The subspace row admits source points and inherited distances, and the Lipschitz-map row exposes the finite graph window and bound that the extension must preserve.

The target side is read through $Y,V$. The inner-product row supplies the target metric seed, while the convex-set row supplies the admitted value surface for extension graph reads.

The ledger and graph clauses are $B,F,R$. The ledger stores the single Lipschitz constant and both source and target distance reads, the graph row stores ambient observations, and the restriction row forces source points to replay the original Lipschitz map.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier has no host extension operator, quotient-function coordinate, choice row, compactness row, or completion theorem coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Kirszbraun extension non-escape]
\label{thm:kirszbraun-extension-nonescape}
Every $\MetricUp$, $\MetricSubspaceUp$, $\LipschitzMapUp$, $\LipschitzExtensionUp$, $\ConvexSetUp$, or $\InnerProductUp$ consumer of an accepted $\KirszbraunExtensionUp$ packet factors through
$$
X,A,L,Y,V,B,F,R,H,C,P,N .
$$
It may read the packet as a finite extension candidate whose graph restricts to the source Lipschitz map and whose target values remain in the displayed convex inner-product row, but it cannot export a host Kirszbraun theorem, a chosen extension operator, a quotient-map equality, countable choice, compactness, or ambient Hilbert completeness.
\end{theorem}
\begin{proof}
Start from the obligation surface of \autoref{thm:kirszbraun-extension-namecert-obligations}. Every accepted consumer route must read the ambient metric, subspace, source Lipschitz map, target inner-product row, convex codomain row, ledger, graph, restriction, transport, replay, provenance, and name rows.

A source-facing consumer reaches the extension only through $A,L,R$. Thus an admitted source point is compared with the original Lipschitz graph before any ambient graph read is treated as an extension value.

A target-facing consumer reaches values only through $Y,V,B,F$. The inner-product row supplies the metric seed, the convex row admits values, and the ledger checks the same Lipschitz constant against displayed distances.

The remaining rows $H,C,P,N$ repack that route. They preserve and name the carrier but do not add a host theorem, operator selector, quotient equality, choice schedule, compactness witness, or completeness principle.
\end{proof}

\closureat{KirszbraunExtensionUp}{seedStr}

\begin{closurestatus}{\KirszbraunExtensionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kirszbraun-extension-carrier}, \autoref{thm:kirszbraun-extension-namecert-obligations}, and \autoref{thm:kirszbraun-extension-nonescape} seed the finite Kirszbraun extension carrier over metric subspace, Lipschitz map, convex target, inner-product target, extension graph, and Lipschitz-ledger rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host Kirszbraun theorem, global Hilbert completeness, quotient equality of functions, selected extension operators, countable choice, compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, subspace inclusion, source Lipschitz admission, convex inner-product target admission, Lipschitz-ledger readback, graph admission, restriction exactness, transport, replay, provenance, and non-escape for BEDC.Derived.KirszbraunExtensionUp.}
  \constructivestory{A $\KirszbraunExtensionUp$ packet is generated from an ambient Metric row, a MetricSubspace source row, a source LipschitzMap row, an InnerProduct target row, a ConvexSet target row, a Lipschitz-constant ledger, an extension graph, a restriction row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
