\chapter{A Concrete Naming Certificate for $\HyperbolicBoundaryShadowUp$}
\label{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}
\origin{ai}

The $\HyperbolicBoundaryShadowUp$ packet realizes the boundary-fixed disk
transport reading of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion}
and \autoref{def:hyperbolic-boundary-fixed-disk-transport} as finite
NameCert rows. It consumes the disk-coordinate carrier of
\autoref{ch:concrete-instances-unitdisk-namecert}, the metric-read surface of
\autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the fixed-boundary
transport route of \autoref{ch:concrete-instances-poincare-boundary-fixed-transport-namecert},
the boundary-tangent horocycle row of
\autoref{ch:concrete-instances-hyperbolic-horocycle-namecert}, and the
flow-style replay surface of \autoref{ch:concrete-instances-dynsystem-namecert}.
The packet names a boundary shadow of transport on a displayed disk surface;
it is not a host ideal-boundary quotient, not a physical cosmology, not a
global flow, and not a completed hyperbolic surface.

\falsifiablePrediction{Every accepted $\HyperbolicBoundaryShadowUp$ read factors through displayed $\UnitDiskUp$, $\HyperbolicMetricUp$, $\PoincareBoundaryFixedTransportUp$, $\HyperbolicHorocycleUp$, $\DynSystemUp$, audit/refusal, provenance, replay, and local $\NameCert$ rows before it exports a boundary-shadow reading.}

\independenceWitness{unitdisk, hyperbolic-metric, poincare-boundary-fixed-transport, hyperbolic-horocycle, dynsystem: the UnitDisk packet records disk coordinates without metric shadowing; the HyperbolicMetric packet records metric reads without a fixed-boundary transport ledger; the PoincareBoundaryFixedTransport packet preserves a boundary anchor without a horocycle shadow; the HyperbolicHorocycle packet records boundary tangency without flow-style replay; and the DynSystem packet records routed evolution without a hyperbolic boundary anchor. None is bijective to $\HyperbolicBoundaryShadowUp$.}

\begin{definition}[Hyperbolic boundary shadow carrier]
\label{def:hyperbolic-boundary-shadow-carrier}
A $\HyperbolicBoundaryShadowUp$ carrier is a finite $\BHist$ packet
$$
S=(D,M,B,T,Q,Y,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ disk-coordinate row for the finite source and
transported observations.
\item $M$ is the $\HyperbolicMetricUp$ metric-read row over the same displayed
disk data.
\item $B$ is the boundary row naming the preserved far-end boundary reading as
finite certificate data.
\item $T$ is the $\PoincareBoundaryFixedTransportUp$ row that transports disk
points while preserving the boundary row $B$.
\item $Q$ is the $\HyperbolicHorocycleUp$ shadow row recording the
boundary-tangent trace left by the transported disk points.
\item $Y$ is the $\DynSystemUp$ flow-style replay row, used only to order the
finite transport observations.
\item $F$ is the audit/refusal row: it records that boundary-shadow reads pass
through $D,M,B,T,Q,Y$ and do not expose a host ideal-boundary quotient,
physical trajectory, or global hyperbolic surface.
\item $H$ records componentwise $\hsame$ transport for disk, metric, boundary,
transport, horocycle shadow, flow replay, audit/refusal, provenance, and local
naming rows.
\item $C$ records displayed $\Cont$ replay from disk observations through
metric readback, boundary preservation, boundary-fixed transport, horocycle
shadowing, flow-style ordering, and audit/refusal.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicBoundaryShadowUp$,
$\UnitDiskUp$, $\HyperbolicMetricUp$, $\PoincareBoundaryFixedTransportUp$,
$\HyperbolicHorocycleUp$, $\DynSystemUp$, $\BHist$, $\hsame$, $\Cont$, and
$\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicBoundaryShadowUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through
$D,M,B,T,Q,Y,F,H,C,P,N$. It has no coordinate for host ideal-boundary equality,
unlogged observer motion, a global flow parameter, physical spacetime, Lean
verification, or bridge checking.
\end{definition}

\begin{theorem}[Hyperbolic boundary shadow NameCert obligations]
\label{thm:hyperbolic-boundary-shadow-namecert-obligations}
For every accepted $\HyperbolicBoundaryShadowUp$ carrier
$S=(D,M,B,T,Q,Y,F,H,C,P,N)$, the local
$\NameCert_{\HyperbolicBoundaryShadowUp}$ surface consists exactly of
disk-coordinate admission, hyperbolic-metric readback, boundary preservation,
boundary-fixed transport, horocycle-shadow exposure, flow-style replay,
audit/refusal exactness, componentwise transport, displayed continuation,
package provenance, and local naming through $D,M,B,T,Q,Y,F,H,C,P,N$.

Every boundary-shadow read from the packet factors through
$$
\UnitDiskUp \longmapsto \HyperbolicMetricUp \longmapsto
\PoincareBoundaryFixedTransportUp \longmapsto \HyperbolicHorocycleUp
\longmapsto \DynSystemUp
$$
together with the boundary, audit/refusal, and structural
$\BHist,\hsame,\Cont,\Pkg,\NameCert$ rows.
\end{theorem}
\begin{proof}
Project the accepted carrier. The disk surface is row $D$, and the
hyperbolic metric readback over that surface is row $M$.

The boundary information is then forced through $B$ and $T$. Row $B$ names the
preserved far-end boundary reading, while row $T$ records transport that keeps
that boundary row fixed in the sense of
\autoref{def:hyperbolic-boundary-fixed-disk-transport}.

The shadow-specific content is row $Q$, read only after the disk, metric,
boundary, and fixed-transport rows have been displayed. Row $Y$ orders the
finite observations as a flow-style replay without adding a global clock.

The audit/refusal row $F$ and the structural rows $H,C,P,N$ exhaust the public
surface. Since no carrier coordinate stores host ideal-boundary equality,
unlogged observer motion, a global flow parameter, or physical spacetime, the
listed rows are exactly the local NameCert obligations.
\end{proof}

\closureat{HyperbolicBoundaryShadowUp}{seedStr}

\begin{closurestatus}{\HyperbolicBoundaryShadowUp}
  \constructivestory{A $\HyperbolicBoundaryShadowUp$ packet is generated from UnitDisk coordinates, HyperbolicMetric readback, a preserved boundary row, PoincareBoundaryFixedTransport, a HyperbolicHorocycle shadow row, DynSystem flow-style replay, audit/refusal data, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-boundary-shadow-carrier} and \autoref{thm:hyperbolic-boundary-shadow-namecert-obligations} seed the finite boundary-shadow route through disk coordinates, metric readback, preserved boundary transport, horocycle shadowing, flow-style replay, audit/refusal, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host ideal-boundary quotient equality, physical spacetime, unlogged observer motion, global hyperbolic flows, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, disk placement, metric readback, boundary preservation, boundary-fixed transport, horocycle-shadow exactness, flow replay, audit/refusal coverage, and local naming for BEDC.Derived.HyperbolicBoundaryShadowUp.}
\end{closurestatus}
