\chapter{A Concrete Naming Certificate for $\CellularSubstrateClassifierBoundaryUp$}
\label{ch:concrete-instances-cellular-substrate-classifier-boundary-namecert}
\origin{ai}

The $\CellularSubstrateClassifierBoundaryUp$ packet realizes the cellular-automaton substrate reading of \autoref{ch:visions-cellular-automaton-substrate-reading} as a finite classifier-boundary carrier. It binds the local transition table, orbit replay, pattern-classifier tag row, closed-observation manifest, and refusal boundary into one NameCert surface. The packet is designed to accept cellular substrate observations only when the classifier that names the observed pattern is displayed as data, so no untagged orbit replay can masquerade as a closed observation.

Before its manifest and closed-observation rows are exported, the packet consumes the rule-table and finite-orbit rows of \autoref{ch:concrete-instances-cellularautomaton-namecert}, the substrate carrier of \autoref{ch:concrete-instances-cellularsubstrate-namecert}, and the classifier comparison surface of \autoref{ch:concrete-instances-cellularsubstrateclassifier-namecert}. These sibling routes determine which local transition, orbit replay, and pattern tag rows may enter the boundary carrier.

The classifier-boundary packet also consumes the observation-window discipline of \autoref{ch:concrete-instances-cellular-substrate-observation-boundary-namecert} and the classifier-row surface of \autoref{ch:concrete-instances-cellularsubstrateclassifier-namecert} before its Rule 110 handoff row is exposed. Thus the closed-observation boundary and the classifier lattice edge are both visible before a universal-substrate read can use the packet.

\begin{definition}[CellularSubstrateClassifierBoundary carrier]
\label{def:cellular-substrate-classifier-boundary-carrier}
A $\CellularSubstrateClassifierBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(L,O,G,M,A,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the local cellular transition row, including the finite alphabet, neighborhood window, and rule table.
\item $O$ is the orbit replay row generated by iterating $L$ over the stated initial row and finite time window.
\item $G$ is the pattern-classifier tag row that assigns each inspected local pattern to a finite tag family.
\item $M$ is the manifest row specifying the accepted observation windows, expected replay checks, and public audit fields.
\item $A$ is the closed-observation admission row, requiring the replayed orbit and the classifier tags to agree on every observed window.
\item $R$ is the Rule 110 substrate handoff row when the local rule is read through the cellular universal-substrate exhibit.
\item $H$ records componentwise $\hsame$ transport for the local rule, orbit replay, classifier tags, manifest, admission row, Rule 110 handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from local transition data through orbit replay, pattern classification, closed-observation admission, and any Rule 110 handoff.
\item $P$ is the $\Pkg$ provenance over $\CellularSubstrateClassifierBoundaryUp$, cellular-automaton substrate reading, Rule 110 substrate, classifier tags, closed observation, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CellularSubstrateClassifierBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for an unclassified orbit, a detached semantic interpretation of a pattern, an induction principle over all time steps, or an observation that bypasses the manifest and classifier rows.
\end{definition}

\begin{theorem}[CellularSubstrateClassifierBoundary NameCert obligations]
\label{thm:cellular-substrate-classifier-boundary-namecert-obligations}
For every accepted $\CellularSubstrateClassifierBoundaryUp$ carrier $B=(L,O,G,M,A,R,H,C,P,N)$, the local $\NameCert_{\CellularSubstrateClassifierBoundaryUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the local transition table, orbit replay, classifier tag row, manifest, closed-observation admission row, optional Rule 110 handoff, transport, replay, provenance, and local naming;
\item local-rule replay, requiring every accepted observation to display $L$ and $O$ before any classifier-boundary claim is consumed;
\item classifier-boundary exposure, requiring the tag row $G$ to be present for each observed pattern window;
\item manifest closure, requiring the row $M$ and admission row $A$ to bind replayed orbits and classifier tags into one finite observation record;
\item Rule 110 handoff discipline, requiring $R$ when the packet is read through the universal cellular substrate route;
\item classifier transport, requiring all accepted comparisons to use only $H$, $C$, $P$, and $N$;
\item ledger refusal, excluding untagged orbit replay, detached semantic interpretation, all-time induction, and observations outside the manifest and classifier rows.
\end{enumerate}
No classifier-boundary obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cellular-substrate-classifier-boundary-carrier}. The accepted packet displays exactly the local rule, orbit replay, classifier tag row, manifest, admission row, Rule 110 handoff, and structural rows.

Local-rule replay comes first. The orbit row $O$ is generated from the transition row $L$, so no accepted observation can be read without displaying the finite rule table and the replay window.

Classifier-boundary exposure and manifest closure then bind the orbit to a tag discipline. The tag row $G$ names the inspected patterns, while $M$ and $A$ require those tags to agree with the manifest's closed-observation checks.

Finally the Rule 110 handoff and structural rows preserve the same route. The optional row $R$ names the universal cellular substrate path when present, and $H,C,P,N$ transport, replay, source, and name the local carrier. Since untagged or detached observations have no row in the packet, they cannot become NameCert obligations.
\end{proof}

\falsifiablePrediction{A packet with a local transition row and orbit replay but no pattern-classifier tag row is rejected by the classifier-boundary carrier.}

\independenceWitness{cellular-automaton-substrate-reading, metacicredexfrontier, rule110substrate, binaire, apophaticname: the packet is not bijective to these siblings because it binds local cellular transition, orbit replay, classifier tags, closed-observation admission, Rule 110 handoff, and classifier-boundary refusal in one finite NameCert route.}

\begin{theorem}[CellularSubstrateClassifierBoundary closed-observation handoff]
\label{thm:cellular-substrate-classifier-boundary-closed-observation-handoff}
Every closed cellular observation accepted by a $\CellularSubstrateClassifierBoundaryUp$ packet reads the route
$$
L,O \longmapsto G \longmapsto M,A \longmapsto R \longmapsto H,C,P,N .
$$
The route starts with a finite local transition rule and orbit replay, passes through the pattern-classifier tag row, binds the result to a manifest and closed-observation admission row, and reaches the Rule 110 handoff only as displayed substrate data. A Lean follow-up for this carrier must supply $\Nontrivial$ and $\FieldFaithful$ instances in \texttt{lean4/BEDC/Derived/CellularSubstrateClassifierBoundaryUp/TasteGate.lean}.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:cellular-substrate-classifier-boundary-carrier}. The rows $L$ and $O$ are the only local-rule and orbit-replay rows, and $G$ is the only classifier row attached to the inspected patterns.

Read manifest admission next. The rows $M$ and $A$ bind the displayed classifier tags to the closed-observation record, so an orbit replay without $G$ cannot pass the admission surface.

The remaining rows preserve the same finite dependency chain. The Rule 110 handoff $R$ is downstream of rule, orbit, classifier, and manifest data, while $H,C,P,N$ transport, replay, source, and name the accepted route. Therefore every accepted observation factors through the classifier boundary.
\end{proof}

\closureat{CellularSubstrateClassifierBoundaryUp}{seedStr}

\begin{closurestatus}{\CellularSubstrateClassifierBoundaryUp}
  \constructivestory{A $\CellularSubstrateClassifierBoundaryUp$ packet is generated from a local cellular transition table, orbit replay, pattern-classifier tags, a closed-observation manifest, an admission row, an optional Rule110Substrate handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cellular-substrate-classifier-boundary-carrier}, \autoref{thm:cellular-substrate-classifier-boundary-namecert-obligations}, and \autoref{thm:cellular-substrate-classifier-boundary-closed-observation-handoff} seed the finite classifier-boundary surface for cellular substrate observations.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close all-time induction, unclassified orbit semantics, a complete Rule 110 bridge, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, local-rule replay, classifier-boundary exposure, manifest closure, Rule 110 handoff discipline, classifier transport, and ledger refusal for BEDC.Derived.CellularSubstrateClassifierBoundaryUp.}
\end{closurestatus}
