\chapter{A Concrete Naming Certificate for $\RegularCauchyTailEnvelopeUp$}
\label{ch:concrete-instances-regular-cauchy-tail-envelope-namecert}
\origin{human}

Following Bishop and Bridges on constructive real numbers by regular Cauchy sequences, the $\RegularCauchyTailEnvelopeUp$ packet names the finite tail-envelope data needed when a regular rational sequence is handed to the $\RealUp$ completion route. It sits between the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the explicit modulus surface of \autoref{ch:concrete-instances-regular-modulus-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is finite tail-control data for the L10 regular-Cauchy route; it is not a selected real limit, quotient sequence, countable-choice schedule, host equality comparison, or ambient completeness theorem.

\begin{definition}[Regular Cauchy tail envelope carrier]
\label{def:regular-cauchy-tail-envelope-carrier}
A $\RegularCauchyTailEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(S,U,D,W,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source regular Cauchy row whose rational entries are read through the $\RegSeqRatUp$ route.
\item $U$ is the unary tail-bound row. For each precision request it records a finite tail index beyond which the source row is inspected.
\item $D$ is the dyadic tolerance ledger, translating the precision request and the chosen tail bound into $\DyadicRatCoreUp$ comparison budgets.
\item $W$ is the finite $\StreamNameUp$ window selected by the tail bound.
\item $R$ is the $\RegSeqRatUp$ readback row that repacks the inspected window as regular rational sequence data.
\item $Q$ is the terminal $\RealUp$ seal row, visible only after $S,U,D,W,R$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the source row, tail bound, dyadic ledger, window, readback, seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from a precision request through $S,U,D,W,R,Q,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyTailEnvelopeUp$, $\RegularModulusUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTailEnvelopeUp}$ row.
\end{enumerate}
The classifier accepts only packets in which the source row, unary tail bound, dyadic ledger, StreamName window, RegSeqRat readback, and Real seal all describe the same displayed regular Cauchy route. No carrier coordinate stores a quotient representative, selected limit, countable-choice schedule, host equality, or ambient $\RealUp$ completeness proof.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyTailEnvelopeUp.RegularCauchyTailEnvelopeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Regular Cauchy tail envelope NameCert obligations]
\label{thm:regular-cauchy-tail-envelope-namecert-obligations}
For every accepted $\RegularCauchyTailEnvelopeUp$ carrier $E=(S,U,D,W,R,Q,H,C,P,N)$, the local $\NameCert_{\RegularCauchyTailEnvelopeUp}$ surface consists exactly of source regular Cauchy admission, unary tail-bound display, dyadic tolerance accounting, finite StreamName window selection, RegSeqRat readback, terminal Real seal routing, componentwise transport, continuation replay, package provenance, and local naming through the rows $S,U,D,W,R,Q,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-tail-envelope-carrier}. The source row $S$ is the only regular Cauchy input, and $U$ is the only tail-bound coordinate attached to it.

The ledger $D$ translates the requested precision and the displayed tail bound into dyadic comparison data. The window row $W$ and readback row $R$ then expose exactly the finite observations consumed by the StreamName and RegSeqRat surfaces.

The seal row $Q$ is downstream of those rows. Transport, replay, provenance, and local naming through $H,C,P,N$ preserve the same finite route, and the excluded quotient, selected-limit, choice, host-equality, and completeness data have no carrier coordinate.
\end{proof}

\begin{theorem}[Regular Cauchy tail envelope handoff]
\label{thm:regular-cauchy-tail-envelope-handoff}
Every $\RegSeqRatUp$, $\RealUp$, or completion-facing consumer of an accepted $\RegularCauchyTailEnvelopeUp$ carrier must read the finite route
$$
S,U,D,W \longmapsto R \longmapsto Q \longmapsto H,C,P,N
$$
before consuming the regular rational row or terminal real-name seal. Thus the tail envelope supplies named finite tail control for the L10 route rather than an informal appeal to a hidden limit, quotient stream, countable-choice schedule, host equality, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with a consumer request for regular rational or real-name data. The packet exposes the source row only as $S$, so the request must first read the tail bound $U$ and the dyadic ledger $D$.

The finite window $W$ is selected from that bound and ledger. The readback row $R$ repacks the same inspected data as $\RegSeqRatUp$ information, so the consumer reaches the regular rational surface only through displayed finite observations.

The terminal seal $Q$ is reached after this readback. The rows $H,C,P,N$ then transport, replay, source, and name the same route; no excluded analytic coordinate is present, so every handoff remains finite BEDC data.
\end{proof}

\closureat{RegularCauchyTailEnvelopeUp}{seedStr}

\begin{closurestatus}{\RegularCauchyTailEnvelopeUp}
  \constructivestory{A $\RegularCauchyTailEnvelopeUp$ packet is generated from a source regular Cauchy row, a unary tail-bound row, a dyadic tolerance ledger, finite StreamName windows, RegSeqRat readback, a RealUp seal boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-tail-envelope-carrier}, \autoref{thm:regular-cauchy-tail-envelope-namecert-obligations}, and \autoref{thm:regular-cauchy-tail-envelope-handoff} seed the finite tail-envelope surface for the L10 RegSeqRat-to-Real route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient sequences, countable choice, host equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tail-bound exactness, dyadic tolerance accounting, StreamName window routing, RegSeqRat readback, Real seal routing, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyTailEnvelopeUp.}
\end{closurestatus}
