\chapter{A Concrete Naming Certificate for $\CauchyNetCompletionUp$}
\label{ch:concrete-instances-cauchynetcompletion-namecert}
\origin{human}

Following Kelley, Moore--Smith, and Bourbaki, the $\CauchyNetCompletionUp$ packet records the directed Cauchy-net completion carrier that sits between the raw $\CauchyNetUp$ directed-window surface and the completion consumers already named by $\MooreSmithCompletionUp$, $\MetricCompletionUp$, and $\UniformCompletionUp$. It consumes the same separated comparison discipline as \autoref{ch:concrete-instances-separatedmetric-namecert} and the same finite numerical readback route as \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}. The chapter names the completion-facing carrier without selecting a limit, quotienting nets, invoking countable choice, asserting host equality of completed objects, importing an ambient completion, or claiming completeness of $\RealUp$.

\begin{definition}[CauchyNetCompletion carrier]
\label{def:cauchy-net-completion-carrier}
A $\CauchyNetCompletionUp$ carrier is a finite $\BHist$ packet
$$
K=(D,W,Q,M,U,S,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the directed-index substrate read by the accepted $\CauchyNetUp$ row.
\item $W$ is the $\CauchyNetUp$ directed-window and common-upper-witness row over $D$.
\item $Q$ is the completion-boundary request attached to the displayed Cauchy-net row.
\item $M$ is the $\MooreSmithCompletionUp$ handoff row, exposing the same directed-net completion boundary to Moore--Smith consumers.
\item $U$ is the $\UniformCompletionUp$ handoff row when the consumer reads entourages rather than metric balls.
\item $S$ is the $\SeparatedMetricUp$ comparison row for comparing two displayed completion-boundary reads.
\item $R$ is the $\RegSeqRatUp$ finite readback row attached to the retained directed windows.
\item $A$ is the $\RealUp$ terminal seal reached only after $D,W,Q,M,U,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the directed substrate, Cauchy-net row, completion-boundary request, Moore--Smith handoff, uniform handoff, separated comparison, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from directed Cauchy-net evidence through completion-boundary reads, separated comparison, regular-rational readback, and the real seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyNetCompletionUp$, $\CauchyNetUp$, $\MooreSmithCompletionUp$, $\MetricCompletionUp$, $\UniformCompletionUp$, $\SeparatedMetricUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyNetCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for a selected limit, quotient nets, countable choice, host equality of completed objects, an ambient completion object, or a completeness theorem for $\RealUp$.
\end{definition}

\begin{theorem}[CauchyNetCompletion NameCert obligations]
\label{thm:cauchy-net-completion-namecert-obligations}
For an accepted $\CauchyNetCompletionUp$ carrier $K=(D,W,Q,M,U,S,R,A,H,C,P,N)$, the local $\NameCert_{\CauchyNetCompletionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the directed substrate, Cauchy-net row, completion-boundary request, Moore--Smith handoff, uniform handoff, separated comparison, regular readback, real seal, transport, replay, provenance, and local naming row;
\item directed-net coverage, requiring every completion-facing request to consume $D$ and $W$ before $Q,M,U,S,R,A$ can be inspected;
\item Moore--Smith handoff, requiring $M$ to expose the same directed-net boundary that \autoref{ch:concrete-instances-moore-smith-completion-namecert} consumes;
\item metric and uniform handoff, requiring $\MetricCompletionUp$ and $\UniformCompletionUp$ consumers to read the boundary through $Q$ and $U$ rather than through an ambient completed object;
\item separated comparison discipline, requiring any comparison of two displayed boundary reads to pass through $S$;
\item numerical readback discipline, requiring $R$ before the terminal $\RealUp$ seal $A$ is inspected;
\item non-escape for selected limits, quotient nets, countable choice, host equality, ambient completion, and $\RealUp$ completeness.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-net-completion-carrier}. The tuple displays exactly the directed substrate, the Cauchy-net window row, the completion-boundary request, the Moore--Smith and uniform handoffs, separated comparison, readback, seal, and structural rows.

Directed-net coverage is the first dependency. A completion-facing request cannot reach $Q,M,U,S,R,A$ until the accepted $\CauchyNetUp$ row $W$ over $D$ has been displayed.

The handoff obligations use the sibling completion chapters. The row $M$ feeds the Moore--Smith completion route, while $Q$ and $U$ feed metric and uniform completion consumers over the same displayed directed windows. The separated comparison row $S$ supplies comparison data without host equality.

Finally $R$ and $A$ provide the finite numerical readback and terminal seal, and $H,C,P,N$ preserve, replay, source, and name the same route. Since the excluded completion principles have no carrier coordinate, they cannot become NameCert obligations.
\end{proof}

\begin{theorem}[CauchyNetCompletion Moore--Smith handoff]
\label{thm:cauchy-net-completion-moore-smith-handoff}
Every $\MooreSmithCompletionUp$, $\MetricCompletionUp$, or $\UniformCompletionUp$ consumer of an accepted $\CauchyNetCompletionUp$ packet reads the directed-net completion boundary through
$$
D,W,Q \longmapsto M,U,S \longmapsto R,A \longmapsto H,C,P,N .
$$
The route starts with the $\CauchyNetUp$ directed-window row, passes through the Moore--Smith, metric, uniform, and separated comparison rows when those consumers are present, and reaches $\RegSeqRatUp$ readback and the $\RealUp$ seal only afterward. No quotient net, selected limit, countable-choice schedule, host equality of completion points, ambient completion object, or $\RealUp$ completeness row bypasses this route.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:cauchy-net-completion-carrier}. The rows $D$ and $W$ are the only directed-net source rows, and $Q$ is the first completion-boundary request attached to them.

Read the sibling handoff next. The Moore--Smith consumer receives $M$, metric completion consumers read the same boundary through $Q$, and uniform completion consumers receive $U$ only as a handoff from the displayed Cauchy-net boundary. Comparisons of displayed boundary reads pass through $S$.

The numerical exit is downstream. The regular rational row $R$ and real seal row $A$ are available only after the directed-net and completion-boundary rows have been replayed, and the structural rows $H,C,P,N$ preserve and name that route.

The carrier inventory contains no selected limit, quotient-net equality, countable-choice selector, host equality, ambient completion, or $\RealUp$ completeness theorem. Thus every accepted completion consumer factors through the displayed route.
\end{proof}

\falsifiablePrediction{If a directed-net completion consumer reads a boundary without first displaying the $\CauchyNetUp$ directed-window row and the Moore--Smith, metric, or uniform handoff row it consumes, it is not a $\CauchyNetCompletionUp$ packet.}

\independenceWitness{cauchynet, moore-smith-completion, metriccompletion, uniformcompletion, separatedmetric, regseqrat, real: the packet is not bijective to these siblings because it binds the directed Cauchy-net carrier, completion-boundary request, sibling handoffs, separated comparison, finite readback, and terminal seal in one local NameCert route.}

\closureat{CauchyNetCompletionUp}{seedStr}

\begin{closurestatus}{\CauchyNetCompletionUp}
  \constructivestory{A $\CauchyNetCompletionUp$ packet is generated from a directed substrate, a CauchyNet directed-window row, a completion-boundary request, MooreSmithCompletion, MetricCompletion, UniformCompletion, SeparatedMetric, RegSeqRat, Real, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-net-completion-carrier}, \autoref{thm:cauchy-net-completion-namecert-obligations}, and \autoref{thm:cauchy-net-completion-moore-smith-handoff} seed the finite directed-net completion carrier between CauchyNet rows and metric or uniform completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient nets, countable choice, host equality of completed objects, ambient completion, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, directed-net coverage, Moore--Smith handoff, metric and uniform handoff, separated comparison discipline, numerical readback discipline, and non-escape for BEDC.Derived.CauchyNetCompletionUp.}
\end{closurestatus}
