\chapter{A Concrete Naming Certificate for $\RealTightnessUp$}
\label{ch:concrete-instances-real-tightness-namecert}
\origin{human}

Following Bishop and Bridges constructive real analysis, the $\RealTightnessUp$ packet records located dyadic trap data over a displayed $\RealUp$ source as finite NameCert evidence. It consumes the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the dyadic rational grid of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the located interval surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, the bounded located-set row of \autoref{ch:concrete-instances-located-bounded-real-set-namecert}, and the regular Cauchy located-order discipline of \autoref{ch:concrete-instances-regular-cauchy-located-order-namecert}. The packet gives later Real and Completion consumers a finite located-tightness route; it is not Heine--Borel, open-cover compactness, trichotomy, countable choice, quotient real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Real tightness carrier]
\label{def:real-tightness-carrier}
A $\RealTightnessUp$ carrier is a finite $\BHist$ packet
$$
Z=(R,D,S,Q,I,B,O,T,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $R$ is the source $\RealUp$ row whose name is being trapped.
\item $D$ is the $\DyadicRatCoreUp$ grid row supplying dyadic endpoints, midpoint refinements, and tolerance comparisons.
\item $S$ is the $\StreamNameUp$ finite-window row for the requested real-name observations.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the same windows and dyadic tolerances.
\item $I$ is the $\LocatedRealIntervalUp$ row recording the current located interval trap.
\item $B$ is the $\LocatedBoundedRealSetUp$ bounded-source row that bounds the admitted trap requests.
\item $O$ is the $\RegularCauchyLocatedOrderUp$ row recording located-order comparisons between the real-name readback and the dyadic trap endpoints.
\item $T$ is the located dyadic trap ledger: a finite list of intervals, dyadic tolerances, inside/outside locator reads, and retained-window witnesses.
\item $H$ records componentwise $\hsame$ transport for $R,D,S,Q,I,B,O,T$ and the structural rows.
\item $C$ records displayed $\Cont$ replay of the real-name read, dyadic trap refinement, located-interval admission, bounded-set read, located-order comparison, and terminal trap ledger.
\item $P$ is the $\Pkg$ provenance over $\RealTightnessUp$, $\RealUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\LocatedRealIntervalUp$, $\LocatedBoundedRealSetUp$, $\RegularCauchyLocatedOrderUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealTightnessUp}$ row.
\end{enumerate}
The carrier has no coordinate for Heine--Borel, open-cover compactness, trichotomy of arbitrary reals, countable choice, quotient real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Real tightness NameCert obligations]
\label{thm:real-tightness-namecert-obligations}
For an accepted $\RealTightnessUp$ carrier $Z=(R,D,S,Q,I,B,O,T,H,C,P,N)$, the local $\NameCert_{\RealTightnessUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the real source, dyadic grid, stream windows, regular rational readback, located interval, bounded located set, located-order row, trap ledger, transport, replay, provenance, and local naming row;
\item dyadic trap exposure, requiring every retained trap in $T$ to display dyadic endpoints from $D$ and the matching finite observation window from $S$;
\item located interval admission, requiring each trap read to pass through $I$ and the bounded-source row $B$ before it can be consumed as a located real interval;
\item regular Cauchy located-order comparison, requiring the readback row $Q$ and the comparison row $O$ to certify the displayed relation between $R$ and the dyadic trap endpoints;
\item replay stability under componentwise $\hsame$ transport and displayed $\Cont$ routes for $R,D,S,Q,I,B,O,T$;
\item nonescape for Heine--Borel, open-cover compactness, trichotomy, countable choice, quotient real equality, and ambient $\RealUp$ completeness.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-tightness-carrier}. The tuple lists exactly the real source, dyadic grid, finite window, regular readback, located interval, bounded-set, located-order, trap, transport, replay, provenance, and naming rows.

Trap exposure is finite. Each trap row in $T$ reads dyadic endpoints and tolerances from $D$, then matches them to the finite observation window named by $S$ and the regular rational readback named by $Q$.

Located admission is downstream of those displayed rows. The located interval row $I$ records the interval trap, while $B$ records that the trap request stays inside the bounded located-set surface available to the consumer.

The comparison step is the located-order row $O$. It compares the regular Cauchy readback of $Q$ with the dyadic endpoints retained in $T$, and it is transported and replayed only by $H$ and $C$.

The carrier inventory contains no coordinate for Heine--Borel, open-cover compactness, trichotomy, countable choice, quotient real equality, or ambient real completeness. Hence the six rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real tightness located trap route]
\label{thm:real-tightness-located-trap-route}
Every $\RealUp$-facing located trap read of an accepted $\RealTightnessUp$ carrier factors through the finite route
$$
R \longmapsto S,Q \longmapsto D,I,B,O \longmapsto T,H,C,P,N .
$$
The route starts with the real-name source, reads finite stream windows and regular rational approximants, opens the dyadic grid and located interval rows, checks boundedness and located order, and only then exports the trap ledger as the named $\RealTightnessUp$ surface. It exports no Heine--Borel theorem, open-cover compactness principle, trichotomy classifier, countable-choice selector, quotient real equality, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Start with an accepted carrier $Z=(R,D,S,Q,I,B,O,T,H,C,P,N)$. The source real-name row is $R$, and the first observable data are the finite windows $S$ and the regular rational readback $Q$ attached to that source.

The dyadic and located stages follow. The row $D$ supplies endpoints and tolerances, $I$ admits the current located interval, $B$ bounds the trap request, and $O$ compares the readback with the displayed endpoints through the regular Cauchy located-order surface.

The trap ledger $T$ is therefore downstream of all numeric and located rows. The structural rows $H,C,P,N$ transport, replay, record provenance, and name that same route without adding a host-level compactness or completeness object.

Since no carrier coordinate stores Heine--Borel, open-cover compactness, trichotomy, countable choice, quotient real equality, or ambient real completeness, every accepted located trap read remains inside the displayed finite route.
\end{proof}

\falsifiablePrediction{Every accepted RealTightnessUp consumer read of a located dyadic trap factors through RealUp, StreamNameUp, RegSeqRatUp, DyadicRatCoreUp, LocatedRealIntervalUp, LocatedBoundedRealSetUp, RegularCauchyLocatedOrderUp, and the local trap ledger before it can be exported.}

\independenceWitness{real, dyadicratcore, regseqrat, streamname, locatedrealinterval, locatedboundedrealset, regularcauchylocatedorder: the packet is not bijective to these siblings because it binds the real source, finite windows, regular readback, dyadic trap grid, located interval, bounded located-set, located-order comparison, and local NameCert row as one located-tightness route.}

\closureat{RealTightnessUp}{seedStr}

\begin{closurestatus}{\RealTightnessUp}
  \constructivestory{A $\RealTightnessUp$ packet is generated from a Real source row, DyadicRatCore grid row, StreamName finite-window row, RegSeqRat readback row, LocatedRealInterval row, LocatedBoundedRealSet row, RegularCauchyLocatedOrder row, located dyadic trap ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-tightness-carrier}, \autoref{thm:real-tightness-namecert-obligations}, and \autoref{thm:real-tightness-located-trap-route} seed the finite located-tightness carrier and trap route for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Heine--Borel, open-cover compactness, trichotomy, countable choice, quotient real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic trap exposure, located interval admission, bounded-source discipline, regular Cauchy located-order comparison, replay stability, and nonescape for BEDC.Derived.RealTightnessUp.}
\end{closurestatus}
