\chapter{A Concrete Naming Certificate for $\DarbouxContinuityUp$}
\label{ch:concrete-instances-darboux-continuity-namecert}
\origin{human}

Darboux/Bishop--Bridges constructive analysis treats interval continuity as a finite route from a closed bounded source interval, through an explicitly continuous graph, into bracketed intermediate-value data before any completed real image is read. The $\DarbouxContinuityUp$ packet records that route over \autoref{ch:concrete-instances-closedboundedinterval-namecert}, \autoref{ch:concrete-instances-continuousmap-namecert}, \autoref{ch:concrete-instances-intermediatevalue-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. It is a local continuity certificate for L10 interval-image consumers, not an open-cover compactness principle, not quotient real equality, and not ambient completeness of $\RealUp$.

\begin{definition}[DarbouxContinuity carrier]
\label{def:darboux-continuity-carrier}
A $\DarbouxContinuityUp$ carrier is a finite $\BHist$ packet
$$
T=(I,G,V,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the closed bounded interval source row, carrying endpoint order, containment, finite-net source, and source-obligation data from $\ClosedBoundedIntervalUp$.
\item $G$ is the continuous-map graph row over the interval source, recording the displayed $\ContinuousMapUp$ modulus, graph, and classifier-compatible point route.
\item $V$ is the intermediate-value crossing row, recording the admitted sign or order crossing data read through $\IntermediateValueUp$.
\item $D$ is the dyadic bracket ledger from $\DyadicRatCoreUp$, recording finite rational brackets for endpoints, graph samples, crossing windows, and tolerance budgets.
\item $R$ is the $\RegSeqRatUp$ readback row for the bracketed endpoint, sample, and crossing observations.
\item $E$ is the terminal $\RealUp$ seal exposed only after $I,G,V,D,R$ have been displayed.
\item $H$ is the componentwise $\hsame$ row for the interval, graph, crossing, bracket, readback, seal, replay, provenance, and local naming data.
\item $C$ records displayed $\Cont$ replay from any interval-continuity consumer through $I,G,V,D,R,E$ and then through the structural rows.
\item $P$ is the $\Pkg$ provenance over $\DarbouxContinuityUp$, $\ClosedBoundedIntervalUp$, $\ContinuousMapUp$, $\IntermediateValueUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DarbouxContinuityUp}$ row.
\end{enumerate}
The carrier has no coordinate for host open covers, selected subcovers, quotient real equality, trichotomy, countable choice, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[DarbouxContinuity NameCert obligations]
\label{thm:darboux-continuity-namecert-obligations}
For every accepted $\DarbouxContinuityUp$ carrier $T=(I,G,V,D,R,E,H,C,P,N)$, the local $\NameCert_{\DarbouxContinuityUp}$ surface consists exactly of closed-interval source admission, continuous-map graph exposure, intermediate-value crossing exposure, dyadic bracket accounting, RegSeqRat readback, Real-seal handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier rows. The interval source $I$, graph row $G$, crossing row $V$, dyadic ledger $D$, readback row $R$, and seal row $E$ are the only analytic rows available to a consumer.

Read the structural rows separately. The transport row $H$ preserves those analytic rows componentwise, while $C$ replays the same displayed route for interval-continuity consumers.

The provenance and naming rows $P,N$ attach the packet to the cited closed-interval, continuous-map, intermediate-value, dyadic, regular-readback, and Real certificates. No excluded cover, quotient, trichotomy, choice, or completeness coordinate is present.
\end{proof}

\begin{theorem}[DarbouxContinuity source route]
\label{thm:darboux-continuity-source-route}
Every $\DarbouxContinuityUp$ consumer that reads an interval-image or crossing value must first enter through the closed bounded interval source of \autoref{ch:concrete-instances-closedboundedinterval-namecert}, then through the continuous graph of \autoref{ch:concrete-instances-continuousmap-namecert}, then through the crossing row of \autoref{ch:concrete-instances-intermediatevalue-namecert}, and only then through the dyadic, RegSeqRat, and Real rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}.
\end{theorem}
\begin{proof}
Start with the source interval row $I$. Its endpoint, containment, finite-net, and readback obligations supply the finite interval boundary before any graph or image row is available.

Next read the graph and crossing rows. The continuous-map row $G$ supplies the displayed modulus and graph route, and $V$ supplies the intermediate-value crossing data relative to that graph.

Finally expose $D,R,E$ through the same route. The dyadic bracket ledger, regular readback, and Real seal are downstream of $I,G,V$, so a consumer cannot start from an ambient interval image or a completed real-value selection.
\end{proof}

\begin{theorem}[DarbouxContinuity graph exposure]
\label{thm:darboux-continuity-graph-exposure}
For every accepted $\DarbouxContinuityUp$ carrier $T=(I,G,V,D,R,E,H,C,P,N)$, the $\ContinuousMapUp$ graph row $G$ is exposed only after the $\ClosedBoundedIntervalUp$ source row $I$ has been displayed. Any crossing read through $V$ depends on that graph exposure and therefore cannot be read as an interval-image fact detached from the source interval and continuous-map graph.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:darboux-continuity-carrier}. The row $I$ is the source interval coordinate, and $G$ is explicitly described as the continuous-map graph row over that source.

Now inspect the crossing row. The row $V$ records intermediate-value crossing data read through the graph row $G$, so a consumer of $V$ must have already displayed both the source interval row and the continuous graph row.

The structural rows $H,C,P,N$ only transport, replay, source, and name this route. They add no detached image coordinate, so every accepted crossing read remains dependent on the $I$ then $G$ exposure order.
\end{proof}

\begin{theorem}[DarbouxContinuity Real-seal handoff]
\label{thm:darboux-continuity-real-seal-handoff}
For every accepted $\DarbouxContinuityUp$ carrier $T=(I,G,V,D,R,E,H,C,P,N)$, the $\RealUp$ row $E$ is terminal. It may be read only after the dyadic bracket ledger $D$ and the $\RegSeqRatUp$ readback row $R$ expose the bracketed endpoint, sample, and crossing observations used by the intermediate-value route.
\end{theorem}
\begin{proof}
Project the analytic rows. The dyadic ledger $D$ stores the finite rational brackets, and the row $R$ is the regular rational readback for those bracketed observations.

The seal row is downstream. In \autoref{def:darboux-continuity-carrier}, $E$ is exposed only after $I,G,V,D,R$ have been displayed, so the completed real-name read cannot precede the bracket ledger or its regular readback.

Transport and replay preserve this terminal position. The rows $H,C,P,N$ can reread the same sealed route for a consumer, but they cannot supply an ambient Real value without the displayed dyadic and regular-rational handoff.
\end{proof}

\begin{theorem}[DarbouxContinuity non-escape]
\label{thm:darboux-continuity-nonescape}
Every accepted $\DarbouxContinuityUp$ packet exports only the finite rows
$$
I,G,V,D,R,E,H,C,P,N.
$$
It exports no host interval image, open-cover compactness object, selected subcover, selected point, quotient real equality, trichotomy decision, countable-choice schedule, or ambient completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Project the packet and inspect the carrier inventory. The analytic rows are the closed interval source, continuous graph, intermediate-value crossing, dyadic bracket ledger, regular readback, and terminal Real seal.

The structural rows do not add analytic content. They only transport, replay, source, and name the same finite route through $H,C,P,N$.

Since no carrier coordinate stores host compactness, quotient equality, a selected point, trichotomy, choice, or ambient completeness, no accepted consumer can extract such data from the Darboux continuity certificate.
\end{proof}

\falsifiablePrediction{An accepted $\DarbouxContinuityUp$ read is refuted if it exposes an interval-image or crossing value without first displaying the closed interval source, continuous graph, intermediate-value crossing, dyadic bracket, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming rows.}

\independenceWitness{closedboundedinterval, continuousmap, intermediatevalue, dyadicratcore, regseqrat, real: none alone is bijective with $\DarbouxContinuityUp$ because the packet jointly records an interval source, continuous graph, crossing ledger, dyadic brackets, regular readback, Real seal, transport, replay, provenance, and local NameCert.}

\closureat{DarbouxContinuityUp}{seedStr}

\begin{closurestatus}{\DarbouxContinuityUp}
  \constructivestory{A $\DarbouxContinuityUp$ packet is generated from a closed bounded interval source, a continuous-map graph, intermediate-value crossing data, a dyadic bracket ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:darboux-continuity-carrier}, \autoref{thm:darboux-continuity-namecert-obligations}, \autoref{thm:darboux-continuity-source-route}, and \autoref{thm:darboux-continuity-nonescape} bind the L10 interval-continuity carrier to closed-interval, continuous-map, intermediate-value, dyadic, regular-readback, and Real-seal source rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Lean verification, bridge checking, open-cover compactness, quotient real equality, trichotomy, selected interval-image points, countable choice, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, graph exposure, crossing-route exactness, dyadic bracket readback, Real-seal handoff, and non-escape for BEDC.Derived.DarbouxContinuityUp.}
\end{closurestatus}
