\chapter{A Concrete Naming Certificate for $\GlobalFiberSpectraUp$}
\label{ch:concrete-instances-global-fiber-spectra-namecert}
\origin{ai}

The $\GlobalFiberSpectraUp$ packet realizes the global fiber-spectrum analysis of \autoref{subsec:philosophy-dna-window-six-boundary-tiles} as finite $Q_{6}$ classifier and edge-spectrum NameCert data. It consumes the codon-window source of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the DNA boundary-tile carrier of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, and the radial wobble spectrum of \autoref{ch:concrete-instances-radial-wobble-spectrum-namecert}. The packet records complete $3+1$ fiber tiles, same-class Hamming edge counts, nucleotide-substitution edge counts, and histogram-baseline rows; it is not a biological law claim, stochastic evolution model, quotient codon semantics, or hidden global classifier oracle.

\begin{definition}[GlobalFiberSpectra carrier]
\label{def:global-fiber-spectra-carrier}
A $\GlobalFiberSpectraUp$ carrier is a finite $\BHist$ packet
$$
G=(Q,F,E,S,N,R,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $Q_{6}$ codon-window source row with the two-axis nucleotide readback.
\item $F$ is the complete global fiber $3+1$ tile row, naming the Ile/Met and Stop/Trp tiles selected by the global-fiber condition.
\item $E$ is the $Q_{1}$ Hamming edge-spectrum row for same-class and cross-class edges by bit direction.
\item $S$ is the single-nucleotide substitution spectrum row by codon position.
\item $N$ is the same-histogram random baseline row for the standard degeneracy histogram.
\item $R$ is the classifier-readback row that ties the finite counts to the displayed standard translation classifier.
\item $H$ records componentwise $\hsame$ transport for codon windows, fiber rows, edge rows, substitution rows, baseline rows, classifier readback, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a finite spectrum request through $Q,F,E,S,N,R$.
\item $P$ is the $\Pkg$ provenance over $\GlobalFiberSpectraUp$, $\CodonSixBitWindowUp$, $\DnaWindowSixBoundaryTileUp$, $\RadialWobbleSpectrumUp$, the source vision \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\GlobalFiberSpectraUp}$ row.
\end{enumerate}
The carrier has no coordinate for a biological necessity claim, an unobserved evolutionary dynamics model, quotient codon equality, infinite sampling, or a classifier not displayed as finite table data.
\end{definition}

\begin{theorem}[GlobalFiberSpectra NameCert obligations]
\label{thm:global-fiber-spectra-namecert-obligations}
For every accepted $\GlobalFiberSpectraUp$ carrier $G=(Q,F,E,S,N,R,H,C,P,L)$, the local $\NameCert_{\GlobalFiberSpectraUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the $Q_{6}$ codon window, complete global fiber tile row, Hamming edge spectrum, substitution edge spectrum, same-histogram baseline, classifier readback, transport, replay, provenance, and local naming;
\item global-fiber exactness, requiring the $3+1$ tile row $F$ to name complete fibers rather than local multiplicity alone;
\item edge-spectrum accounting, requiring $E$ and $S$ to count displayed finite edge families over the same classifier row $R$;
\item histogram-baseline separation, requiring $N$ to remain a comparison row and not a stochastic generation model;
\item sibling compatibility, requiring downstream trigger or wobble consumers to read this packet through the codon-window, boundary-tile, and radial-spectrum sibling rows;
\item ledger non-escape, excluding biological necessity, hidden classifier semantics, quotient codon equality, infinite sampling, and unbounded evolutionary dynamics.
\end{enumerate}
No global fiber-spectrum obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:global-fiber-spectra-carrier}. The rows $Q,F,E,S,N,R,H,C,P,L$ are the full finite inventory available to an accepted spectrum consumer.

The global-fiber row $F$ is read over the displayed classifier row $R$ and codon window $Q$, so the $3+1$ tiles are complete fiber data rather than detached local examples. The edge rows $E$ and $S$ are also counted over the same displayed classifier.

The baseline row $N$ is only a comparison ledger. Transport, replay, provenance, and local naming are supplied by $H,C,P,L$, and no biological, quotient, hidden-classifier, or infinite-sampling coordinate appears in the carrier. Hence the listed rows exhaust the NameCert obligations.
\end{proof}

\falsifiablePrediction{A candidate packet that lists local $3+1$ faces but does not display the complete global fiber row $F$ is rejected by the $\GlobalFiberSpectraUp$ carrier.}

\independenceWitness{codon-six-bit-window, dna-window-six-boundary-tile, radial-wobble-spectrum, six-boundary-tile-coverage: none is bijective to $\GlobalFiberSpectraUp$ because this packet jointly carries complete global fibers, Hamming edge spectra, substitution spectra, histogram baseline rows, classifier readback, transport, replay, provenance, and local naming.}

\closureat{GlobalFiberSpectraUp}{seedStr}

\begin{closurestatus}{\GlobalFiberSpectraUp}
  \constructivestory{A $\GlobalFiberSpectraUp$ packet is generated from a displayed Q6 codon window, complete global fiber tile rows, Hamming edge spectra, nucleotide-substitution spectra, same-histogram baseline rows, classifier readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:global-fiber-spectra-carrier} and \autoref{thm:global-fiber-spectra-namecert-obligations} seed the finite global fiber-spectrum packet over displayed Q6 classifier and edge-spectrum rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, biological necessity, stochastic evolution, quotient codon equality, infinite sampling, or hidden classifier semantics.}
  \upgradepath{Obligation closure requires checked carrier admission, global-fiber exactness, edge-spectrum accounting, histogram-baseline separation, sibling compatibility, and ledger non-escape for BEDC.Derived.GlobalFiberSpectraUp.}
\end{closurestatus}
