\chapter{A Concrete Naming Certificate for $\DuhamelPrincipleUp$}
\label{ch:concrete-instances-duhamel-principle-namecert}
\origin{human}

Following Pazy's semigroup treatment of evolution equations and Evans' variation-of-constants discussion for forced linear problems, the $\DuhamelPrincipleUp$ packet records the finite BEDC route by which a homogeneous evolution row, a forcing row, and an integral convolution row are read as one solution handoff. It sits after the real-time surface of \autoref{ch:concrete-instances-real-namecert}, the integration interface of \autoref{ch:concrete-instances-integral-namecert}, the ODE local-flow source of \autoref{ch:concrete-instances-ode-namecert}, the dynamical-system flow packet of \autoref{ch:concrete-instances-dynsystem-namecert}, and the semigroup associativity surface of \autoref{ch:concrete-instances-semigroup-namecert}. The carrier names the forcing route; it does not assert a host solution operator, classical existence theorem, quotient trajectory equality, or choice-selected mild solution.

\begin{definition}[DuhamelPrinciple carrier]
\label{def:duhamel-principle-carrier}
A $\DuhamelPrincipleUp$ carrier is a finite $\BHist$ packet
$$
D=(T,E,F,G,I,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\RealUp$ time-window row, including the initial time, endpoint time, and inspected finite subintervals.
\item $E$ is the homogeneous evolution row, read as an $\OdeUp$ local-flow or $\DynSystemUp$ flow packet and constrained by the $\SemigroupUp$ composition ledger.
\item $F$ is the forcing-data row, recording the displayed inhomogeneous source samples and their $\RealUp$ readbacks.
\item $G$ is the propagator action row, pairing each displayed forcing sample with the elapsed-time evolution row that carries it toward the endpoint.
\item $I$ is the $\IntegralUp$ convolution row over the finite time window, with its partition, approximation, and endpoint ledgers visible as integral data.
\item $S$ is the solution readback row, exposing the homogeneous contribution and the integral forcing contribution as the endpoint history inspected by downstream consumers.
\item $H$ records componentwise $\hsame$ transport for time windows, evolution rows, forcing rows, propagator rows, integral rows, solution readbacks, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a Duhamel request through $T,E,F,G,I,S,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DuhamelPrincipleUp$, $\RealUp$, $\OdeUp$, $\DynSystemUp$, $\SemigroupUp$, $\IntegralUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DuhamelPrincipleUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,E,F,G,I,S,H,C,P,N$. It has no coordinate for a host semigroup on a completed function space, an unobserved Bochner integral, a selected solution operator, classical choice, quotient trajectory equality, or global well-posedness.
\end{definition}

\begin{theorem}[DuhamelPrinciple NameCert obligations]
\label{thm:duhamel-principle-namecert-obligations}
For every accepted $\DuhamelPrincipleUp$ carrier $D=(T,E,F,G,I,S,H,C,P,N)$, the local $\NameCert_{\DuhamelPrincipleUp}$ obligation surface consists exactly of real-time window admission, homogeneous evolution readback, forcing-data admission, propagator action exposure, $\IntegralUp$ convolution readback, endpoint solution readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through the displayed rows.
\end{theorem}
\begin{proof}
Project the finite carrier. The time row $T$ fixes the inspected interval before the evolution, forcing, or convolution rows are read. The homogeneous row $E$ is already a named ODE or dynamical-system flow route, and its semigroup composition behavior is visible only through the displayed $\SemigroupUp$ ledger.

Read the forcing and propagator rows next. The row $F$ supplies the inhomogeneous samples and real readbacks, while $G$ records how the displayed evolution row carries each sample toward the endpoint. No host trajectory space is introduced at this stage.

The integral row $I$ is then the only source of convolution data. Its partition, approximation, and endpoint ledgers are inherited from $\IntegralUp$, and the solution row $S$ may inspect only the homogeneous contribution together with that displayed convolution endpoint.

Finally use $H$ and $C$ to transport and replay the same finite rows, and use $P$ and $N$ for provenance and local naming. Since all excluded analytic objects lack carrier coordinates, they cannot enter the local NameCert obligation surface.
\end{proof}

\begin{theorem}[DuhamelPrinciple forcing route]
\label{thm:duhamel-principle-forcing-route}
Every downstream $\OdeUp$, $\DynSystemUp$, stability, or PDE consumer of an accepted $\DuhamelPrincipleUp$ packet reads the inhomogeneous contribution through the finite route
$$
T,E,F,G\longmapsto I\longmapsto S\longmapsto H,C,P,N.
$$
Thus the forced endpoint is available only as homogeneous evolution plus the displayed $\IntegralUp$ convolution of forcing data against the propagator row. The route exports no host solution operator, unbounded semigroup theorem, chosen mild solution, quotient trajectory equality, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with a forcing-facing consumer. The real-time row $T$ and the homogeneous evolution row $E$ determine the displayed elapsed-time cells and the semigroup-style composition ledger available to the packet.

Read $F$ and $G$ after that boundary is fixed. The forcing samples are paired with visible propagator action rows, so the consumer sees only finitely displayed source observations and their transported endpoint contributions.

The convolution is then read from $I$. This invokes the $\IntegralUp$ carrier and ledger discipline over the same time window, so partitions and approximations remain integral rows rather than hidden choices.

The endpoint row $S$ repacks the homogeneous part and the forcing convolution as the public readback. Transport, replay, provenance, and naming are supplied by $H,C,P,N$, which preserve the same route and leave every absent analytic object outside the carrier.
\end{proof}

\closureat{DuhamelPrincipleUp}{seedStr}

\begin{closurestatus}{\DuhamelPrincipleUp}
  \constructivestory{A $\DuhamelPrincipleUp$ packet is generated from a RealUp time window, homogeneous ODE or DynSystem evolution row, Semigroup composition ledger, forcing-data row, propagator action row, IntegralUp convolution row, solution readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:duhamel-principle-carrier}, \autoref{thm:duhamel-principle-namecert-obligations}, and \autoref{thm:duhamel-principle-forcing-route} seed the finite variation-of-constants carrier, obligation surface, and forcing route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host solution operators, unbounded semigroup theorems, chosen mild solutions, quotient trajectory equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, forcing-route exactness, IntegralUp convolution readback, evolution transport stability, solution nonescape, and TasteGate field faithfulness for BEDC.Derived.DuhamelPrincipleUp.}
\end{closurestatus}
