\chapter{A Concrete Naming Certificate for $\DedekindGapLocatedCutUp$}
\label{ch:concrete-instances-dedekind-gap-located-cut-namecert}
\origin{human}

Following Bishop and Bridges constructive located cuts, the $\DedekindGapLocatedCutUp$ packet records the finite lower-upper separation data that a completion or real-comparison consumer may inspect before any construction of $\RealUp$ is claimed. It is a located-cut boundary over the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational sequence route of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the located-supremum consumer surface of \autoref{ch:concrete-instances-locatedsupremum-namecert}. The packet supplies a gap-located comparison boundary consumed by $\RegSeqRatUp$ and $\RealUp$ readers; it is not a Dedekind construction of $\RealUp$, not quotient equality of cuts, and not an ambient completeness principle.

\begin{definition}[Dedekind gap located cut carrier]
\label{def:dedekind-gap-located-cut-carrier}
A $\DedekindGapLocatedCutUp$ carrier is a finite $\BHist$ packet
$$
G=(L,U,D,W,R,S,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the lower-cut ledger: finite rational cells certified to lie below the boundary.
\item $U$ is the upper-cut ledger: finite rational cells certified to lie above the boundary.
\item $D$ is the $\DyadicRatCoreUp$ gap row. For every displayed tolerance request it names a dyadic bracket or a separating dyadic cell between the currently exposed lower and upper ledgers.
\item $W$ is the $\StreamNameUp$ observation schedule for the finite lower, upper, and gap requests actually read by a consumer.
\item $R$ is the $\RegSeqRatUp$ readback row, repacking the windowed lower-upper data as regular rational observations.
\item $S$ is the $\LocatedSupremumUp$ boundary handoff row available to consumers that need an upper-bound or lower-approximation surface.
\item $E$ is the terminal $\RealUp$ seal row. It is exposed only after $L,U,D,W,R,S$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for lower cells, upper cells, dyadic gaps, stream windows, regular readback, located-supremum handoff, real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay through the ordered route $L,U,D,W,R,S,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DedekindGapLocatedCutUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedSupremumUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindGapLocatedCutUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,U,D,W,R,S,E,H,C,P,N$. It has no coordinate for quotient equality of cuts, a selected real representative, countable choice, trichotomy, a host order-completeness theorem, or a Dedekind construction of $\RealUp$.
\end{definition}

\begin{theorem}[Dedekind gap located cut carrier boundary]
\label{thm:dedekind-gap-located-cut-carrier}
Every accepted $\DedekindGapLocatedCutUp$ carrier is read through the displayed route
$$
L,U,D,W,R,S,E,H,C,P,N .
$$
Thus a consumer receives lower-cut cells, upper-cut cells, dyadic gap witnesses, finite stream windows, regular rational readback, a located-supremum boundary handoff, a terminal Real seal, transport, replay, provenance, and local naming. No accepted read exposes quotient equality of lower-upper cuts, a selected real representative, trichotomy, countable choice, ambient completeness, or a construction of $\RealUp$ from Dedekind cuts.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dedekind-gap-located-cut-carrier}. The rows $L$ and $U$ are the only lower and upper cut data, while $D$ supplies the finite dyadic gap evidence inspected by the request.

The rows $W$ and $R$ place those gap observations inside a finite observation schedule and regular rational readback. The located-supremum row $S$ is downstream of the same windowed data, and the real seal $E$ is reached only after that route is displayed.

The structural rows $H,C,P,N$ transport, replay, source, and name the same finite packet. Since the excluded objects are not fields of the carrier, no consumer can recover them from an accepted $\DedekindGapLocatedCutUp$ read.
\end{proof}

\begin{theorem}[Dedekind gap located cut obligations]
\label{thm:dedekind-gap-located-cut-obligations}
For an accepted $\DedekindGapLocatedCutUp$ carrier $G=(L,U,D,W,R,S,E,H,C,P,N)$, the local $\NameCert_{\DedekindGapLocatedCutUp}$ surface consists exactly of carrier admission for the lower and upper ledgers, dyadic gap exposure, StreamName window exposure, RegSeqRat readback, LocatedSupremum boundary handoff, Real seal exposure, componentwise transport, displayed replay, provenance, and local naming. The obligations do not include a quotient of cuts, a host real equality test, selected supremum data outside $S$, or any completeness assertion for $\RealUp$.
\end{theorem}
\begin{proof}
Carrier admission lists the rows $L,U,D,W,R,S,E,H,C,P,N$, so the local NameCert surface begins with a finite inventory rather than an external real construction.

The computational obligations are read in order. Dyadic gap exposure comes from $D$, window discipline from $W$, regular rational readback from $R$, and the upper-bound or lower-approximation consumer handoff from $S$ before the terminal seal $E$ can be consumed.

Transport and replay do not enlarge the inventory. The rows $H$ and $C$ preserve the same displayed data, while $P$ and $N$ record provenance and local naming, so the listed obligations exhaust the accepted packet.
\end{proof}

\begin{theorem}[Dedekind gap RegSeqRat boundary]
\label{thm:dedekind-gap-regseqrat-boundary}
Every $\RegSeqRatUp$ or $\RealUp$-facing read of an accepted $\DedekindGapLocatedCutUp$ packet factors through the finite route
$$
L,U \longmapsto D \longmapsto W \longmapsto R \longmapsto S \longmapsto E .
$$
The route exposes a located lower-upper gap boundary that $\RegSeqRatUp$ and $\RealUp$ consumers may use for comparison work. It does not identify cuts by quotient equality, select a representing real, assert a Dedekind construction of $\RealUp$, or import ambient order completeness.
\end{theorem}
\begin{proof}
Start with the lower and upper ledgers $L,U$. A consumer sees only the displayed finite cells, so the request is a boundary read rather than an equality of cuts.

The dyadic row $D$ supplies the gap witness requested at the displayed precision, and $W$ records the finite observation window in which that witness is inspected. The readback row $R$ then repacks the same window as regular rational sequence data.

The located-supremum handoff $S$ and terminal seal $E$ remain downstream of those rows. Consequently every RegSeqRat or Real-facing read is a routed boundary read, with no coordinate for the excluded quotient, selection, construction, or completeness claims.
\end{proof}

\falsifiablePrediction{An accepted $\DedekindGapLocatedCutUp$ read is refuted if a RegSeqRat or Real-facing consumer can remove the lower ledger, upper ledger, dyadic gap row, StreamName window, RegSeqRat readback, LocatedSupremum handoff, Real seal, transport, replay, provenance, or local naming while preserving the same packet claim.}

\independenceWitness{dyadicratcore, streamname, regseqrat, real, locatedsupremum: $\DedekindGapLocatedCutUp$ is not bijective to any listed sibling because it jointly carries lower and upper cut ledgers, dyadic gap witnesses, finite observation windows, regular rational readback, located-supremum handoff, Real sealing, transport, replay, provenance, and local naming.}

\closureat{DedekindGapLocatedCutUp}{seedStr}

\begin{closurestatus}{\DedekindGapLocatedCutUp}
  \constructivestory{A $\DedekindGapLocatedCutUp$ packet is generated from lower-cut ledgers, upper-cut ledgers, dyadic gap witnesses, StreamName windows, RegSeqRat readback, a LocatedSupremum boundary handoff, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-gap-located-cut-carrier}, \autoref{thm:dedekind-gap-located-cut-carrier}, \autoref{thm:dedekind-gap-located-cut-obligations}, and \autoref{thm:dedekind-gap-regseqrat-boundary} seed the L10 located-cut boundary consumed by RegSeqRat and Real-facing comparison packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a Dedekind construction of RealUp, quotient equality of cuts, selected real representatives, trichotomy, countable choice, ambient order completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, lower-upper gap exposure, dyadic tolerance transport, StreamName window discipline, RegSeqRat readback, LocatedSupremum handoff, and Real seal nonescape for BEDC.Derived.DedekindGapLocatedCutUp.}
\end{closurestatus}
