\chapter{A Concrete Naming Certificate for $\MonotoneConvergenceRealUp$}
\label{ch:concrete-instances-monotone-convergence-real-namecert}
\origin{human}

Following Bishop and Bridges on bounded monotone real sequences, the $\MonotoneConvergenceRealUp$ packet records the finite NameCert surface by which monotone inspection rows, bounded sequence rows, and located-supremum rows meet before any ambient completeness theorem for $\RealUp$ is available. It consumes the bounded sequence carrier of \autoref{ch:concrete-instances-boundedrealsequence-namecert}, the located upper-bound surface of \autoref{ch:concrete-instances-locatedsupremum-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a located-supremum route for bounded monotone RealUp sequences; it is not a proof of full RealUp completeness, a host supremum construction, a trichotomy decision, quotient real equality, countable choice, or a selected limit operator.

\begin{definition}[Monotone convergence real carrier]
\label{def:monotone-convergence-real-carrier}
A $\MonotoneConvergenceRealUp$ carrier is a finite $\BHist$ packet
$$
M=(B,O,U,A,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the source $\BoundedRealSequenceUp$ row, exposing only the finite sequence schedule, stream windows, regular readback, RealUp seal, and closed bounded interval-net bound already named in \autoref{def:bounded-real-sequence-carrier}.
\item $O$ is the monotonicity ledger, recording for the inspected index pairs that the displayed sequence windows are nondecreasing through the same comparison route used by the bounded sequence carrier.
\item $U$ is the $\LocatedSupremumUp$ upper-bound row attached to the bounded range displayed by $B$ and to the comparison rows recorded in $O$.
\item $A$ is the lower-approximation ledger, saying that each requested tolerance window receives a displayed sequence index whose regular-rational readback approaches the located-supremum row from below.
\item $W$ is the shared $\StreamNameUp$ precision-window row used to inspect the source sequence, monotonicity ledger, upper-bound row, and approximation ledger.
\item $R$ is the $\RegSeqRatUp$ readback row for the inspected windows in $W$.
\item $E$ is the terminal $\RealUp$ seal reached only after $B,O,U,A,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the bounded source, monotonicity ledger, located-supremum row, approximation ledger, precision windows, regular readback, real seal, replay, provenance, and local naming row.
\item $C$ records displayed $\Cont$ replay from bounded sequence inspection through monotonicity, located-supremum access, lower approximation, regular readback, and the RealUp seal.
\item $P$ is the $\Pkg$ provenance over $\MonotoneConvergenceRealUp$, $\BoundedRealSequenceUp$, $\LocatedSupremumUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\MonotoneConvergenceRealUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through $B,O,U,A,W,R,E,H,C,P,N$. It has no coordinate for full $\RealUp$ completeness, a host-level supremum, trichotomy, quotient real equality, countable choice, or a selected-limit functional.
\end{definition}

\begin{theorem}[Monotone convergence real NameCert obligations]
\label{thm:monotone-convergence-real-namecert-obligations}
For every accepted $\MonotoneConvergenceRealUp$ carrier $M=(B,O,U,A,W,R,E,H,C,P,N)$, the local $\NameCert_{\MonotoneConvergenceRealUp}$ obligations are exhausted by the following finite rows: carrier admission for the eleven displayed coordinates; bounded-source exposure through $B$; monotonicity inspection through $O$; located upper-bound access through $U$; lower-approximation cofinality through $A$; shared finite-window accounting through $W$; regular-rational readback through $R$; terminal RealUp sealing through $E$; componentwise transport through $H$; continuation replay through $C$; package provenance through $P$; and local naming through $N$.

No obligation may call on a full completeness principle for $\RealUp$, a host supremum object, trichotomy, quotient real equality, countable choice, or a selected limit.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:monotone-convergence-real-carrier}. The source sequence is visible only through the bounded sequence row $B$, and the monotonicity information is visible only through the displayed comparison ledger $O$.

The located-supremum side is then read through $U$ and $A$. The row $U$ supplies the upper-bound surface, while $A$ supplies the lower approximants requested by the finite window row $W$.

Finally the readback and seal rows $R$ and $E$ repack the same inspected data as regular-rational and RealUp observations. The structural rows $H,C,P,N$ transport, replay, source, and name this route, so the listed rows exhaust the local certificate.
\end{proof}

\begin{theorem}[Monotone convergence real located-supremum route]
\label{thm:monotone-convergence-real-located-supremum-route}
Every $\RealUp$ consumer of an accepted $\MonotoneConvergenceRealUp$ carrier reaches the candidate monotone limit only through
$$
B,O,U,A,W,R,E,H,C,P,N.
$$
The route first reads the bounded real sequence row, then the monotonicity ledger, then the located-supremum upper-bound and lower-approximation rows, then the shared finite windows and regular rational readback, and only then the terminal RealUp seal. Consequently the consumer receives a located-supremum route for the displayed bounded monotone sequence rather than full RealUp completeness, a host supremum, trichotomy, quotient real equality, countable choice, or a selected limit.
\end{theorem}
\begin{proof}
Start with the bounded sequence surface. By \autoref{def:bounded-real-sequence-carrier}, a downstream consumer can inspect only the finite sequence schedule, stream windows, regular readback, real seal, closed bounded interval-net bound, and structural naming rows carried by $B$.

Add the monotonicity ledger $O$. It compares only the inspected windows of the same bounded source, so it cannot introduce an unbounded stream, a quotient sequence, or a host order principle.

Now apply the located-supremum surface of \autoref{ch:concrete-instances-locatedsupremum-namecert}. The rows $U$ and $A$ provide upper-bound access and lower-approximation cofinality for the same windowed route.

The final handoff passes through $W,R,E,H,C,P,N$. Since these rows are the only remaining public coordinates, the RealUp consumer obtains only the stated located-supremum route and none of the excluded completeness or choice principles.
\end{proof}

\closureat{MonotoneConvergenceRealUp}{seedStr}

\begin{closurestatus}{\MonotoneConvergenceRealUp}
  \constructivestory{A $\MonotoneConvergenceRealUp$ packet is generated from a bounded RealUp sequence row, a monotonicity ledger, a LocatedSupremumUp upper-bound row, a lower-approximation ledger, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:monotone-convergence-real-carrier}, \autoref{thm:monotone-convergence-real-namecert-obligations}, and \autoref{thm:monotone-convergence-real-located-supremum-route} seed the finite located-supremum route for bounded monotone RealUp sequences.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close full RealUp completeness, a host supremum construction, trichotomy, quotient real equality, countable choice, selected limits, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, bounded-source exposure, monotonicity ledger stability, located-supremum access, lower-approximation cofinality, readback sealing, transport, replay, provenance, and local naming for BEDC.Derived.MonotoneConvergenceRealUp.}
\end{closurestatus}
