\chapter{A Concrete Naming Certificate for $\MetricCompletionAdjunctionUp$}
\label{ch:concrete-instances-metric-completion-adjunction-namecert}
\origin{human}

Following Bishop and Bridges and Kelley on metric completion, the $\MetricCompletionAdjunctionUp$ packet records the universal mapping boundary for a displayed metric source and its completion as finite BEDC data. It reads the metric-completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the dense embedding route of \autoref{ch:concrete-instances-metric-completion-dense-embedding-namecert}, the Cauchy adjunction surface of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert}, and the unit-triangle ledger of \autoref{ch:concrete-instances-completion-unit-triangle-namecert}. The chapter names the metric-specific adjunction packet without quotient completion, selected representatives, countable choice, host equality of completed objects, or ambient completeness.

\begin{definition}[MetricCompletionAdjunction carrier]
\label{def:metric-completion-adjunction-carrier}
A $\MetricCompletionAdjunctionUp$ carrier is a finite $\BHist$ packet
$$
A=(X,M,D,U,K,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source metric row, carrying the displayed carrier, distance classifier, finite balls, and the $\MetricUp$ provenance needed before completion is read.
\item $M$ is the $\MetricCompletionUp$ completion row of \autoref{ch:concrete-instances-metriccompletion-namecert}, including the chosen Cauchy-filter or Cauchy-net branch, readback row, separated comparison, and uniform-completion handoff.
\item $D$ is the $\MetricCompletionDenseEmbeddingUp$ row of \autoref{ch:concrete-instances-metric-completion-dense-embedding-namecert}, displaying the source-to-completion dense image used by the universal mapping read.
\item $U$ is the unit row sending each displayed source point into the completion packet through $D$ and $M$.
\item $K$ is the counit row for completion-facing consumers whose target is already read through the same metric completion surface.
\item $T$ is the triangle ledger. It records that the unit followed by the counit, and the counit followed by the unit-facing extension, replay the same finite rows rather than invoking host equality of completed carriers.
\item $R$ is the $\RegSeqRatUp/\RealUp$ seal row used by the readback side of the completion packet.
\item $E$ is the $\UniformCompletionUp$ and extension-consumer row through which uniformly continuous finite-window maps read the same adjunction packet.
\item $H$ records componentwise $\hsame$ transport for the source metric, completion row, dense embedding, unit, counit, triangle ledger, readback seal, extension row, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from the source metric through dense embedding, unit, completion readback, extension, counit, and triangle comparison.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionAdjunctionUp$, $\MetricCompletionUp$, $\MetricCompletionDenseEmbeddingUp$, $\CauchyCompletionAdjunctionUp$, $\CompletionUnitTriangleUp$, $\RegSeqRatUp$, $\RealUp$, $\UniformCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricCompletionAdjunctionUp}$ row.
\end{enumerate}
The classifier accepts only packets whose unit, counit, and triangle rows are read through the same displayed source metric, completion packet, dense embedding, regular readback, Real seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local NameCert rows.
\end{definition}

\begin{theorem}[MetricCompletionAdjunction NameCert obligations]
\label{thm:metric-completion-adjunction-namecert-obligations}
For every accepted $\MetricCompletionAdjunctionUp$ carrier
$$
A=(X,M,D,U,K,T,R,E,H,C,P,N),
$$
the local $\NameCert_{\MetricCompletionAdjunctionUp}$ surface consists exactly of source metric admission, metric-completion admission, dense embedding exposure, unit visibility, counit visibility, triangle-ledger comparison, RegSeqRat/Real seal readback, uniform-extension handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through the rows of $A$. No obligation may be discharged by a quotient completion, selected Cauchy limit, countable-choice schedule, host equality of completion classes, or ambient complete metric space.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-adjunction-carrier}. The analytic rows are precisely the source metric $X$, completion packet $M$, dense embedding $D$, unit $U$, counit $K$, triangle ledger $T$, readback seal $R$, and extension row $E$.

The dense embedding and completion rows force the order of every accepted read. A consumer first opens the source metric and metric-completion packet, then reads the dense image route before any unit, counit, triangle, Real-seal, or uniform-extension coordinate is available.

Transport and replay are structural. The row $H$ compares only the displayed components by $\hsame$, while $C$ replays the same route through source, dense image, completion, extension, counit, and triangle rows.

Finally $P$ and $N$ source and name the same finite packet. Since none of the listed rows stores a quotient completion, selected limit, countable-choice schedule, host equality, or ambient complete metric space, the displayed obligations exhaust the NameCert surface.
\end{proof}

\begin{theorem}[MetricCompletionAdjunction unit-counit triangle]
\label{thm:metric-completion-adjunction-unit-counit-triangle}
Every unit-counit triangle read of an accepted $\MetricCompletionAdjunctionUp$ carrier factors through the finite route
$$
X \longmapsto D \longmapsto U \longmapsto M \longmapsto E \longmapsto K \longmapsto T \longmapsto R,H,C,P,N .
$$
The route identifies the two triangle faces only by the displayed $\hsame$ and $\Cont$ rows carried in $H$ and $C$, and it consumes the RegSeqRat/Real seal row $R$ only after the metric completion, dense embedding, unit, counit, and uniform-extension rows have been displayed.
\end{theorem}
\begin{proof}
Start from the carrier inventory. The source metric row $X$ and dense embedding row $D$ are the only rows that introduce source points into the completion packet, so the unit face must pass through them before it can reach $M$.

The extension and counit faces are then downstream of the same completion packet. The row $E$ records the uniform-extension consumer route, $K$ records the counit-facing return, and $T$ records the triangle comparison over those already displayed rows.

The terminal seal and structural rows cannot change the route. The row $R$ is the RegSeqRat/Real readback attached to the completion packet, while $H,C,P,N$ only transport, replay, source, and name the same finite data. Therefore the triangle read is exhausted by the displayed route and imports no quotient, selector, choice, host equality, or ambient-completeness coordinate.
\end{proof}

\closureat{MetricCompletionAdjunctionUp}{seedStr}

\begin{closurestatus}{\MetricCompletionAdjunctionUp}
  \constructivestory{A $\MetricCompletionAdjunctionUp$ packet is generated from a source metric row, metric-completion row, dense embedding row, unit row, counit row, triangle ledger, RegSeqRat/Real seal readback, uniform-extension handoff, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-adjunction-carrier}, \autoref{thm:metric-completion-adjunction-namecert-obligations}, and \autoref{thm:metric-completion-adjunction-unit-counit-triangle} seed the metric-specific completion adjunction boundary over dense embedding, unit, counit, triangle, readback, and uniform-extension rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected limits, countable choice, host equality of completed objects, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense embedding exposure, unit and counit visibility, triangle comparison, RegSeqRat/Real seal handoff, uniform-extension handoff, transport, replay, provenance, and local naming for BEDC.Derived.MetricCompletionAdjunctionUp.}
\end{closurestatus}
