\chapter{A Concrete Naming Certificate for $\PerfectSetUp$}
\label{ch:concrete-instances-perfect-set-namecert}
\origin{human}

Following Cantor and Bendixson, the $\PerfectSetUp$ packet names the finite certificate surface for a closed set whose every displayed point remains a derived point. It sits over the open-neighborhood discipline of \autoref{ch:concrete-instances-topology-namecert}, the compact metric inspection rows of \autoref{ch:concrete-instances-compactmetric-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the derivative-stage route of \autoref{ch:concrete-instances-cantor-bendixson-namecert}. The chapter isolates the reusable perfect-kernel face consumed by Cantor-Bendixson analysis; it is not a transfinite decomposition, a selected point enumeration, quotient real equality, or an ambient completeness theorem.

\begin{definition}[PerfectSet carrier]
\label{def:perfect-set-carrier}
A $\PerfectSetUp$ carrier is a finite $\BHist$ packet
$$
S=(T,K,D,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the topology row, carrying the open-neighborhood tests and closed-set complement reads through \autoref{ch:concrete-instances-topology-namecert}.
\item $K$ is the compact-metric source row, carrying the finite metric inspection and cover data supplied by \autoref{ch:concrete-instances-compactmetric-namecert}.
\item $D$ is the derived-point ledger. For every displayed point read from the set and every finite neighborhood request, it records a second compatible point read through the same topology and metric rows.
\item $W$ is the finite window schedule for neighborhood, metric, and derived-point requests.
\item $R$ is the regular rational readback row used by the metric comparisons and the non-isolation witnesses.
\item $E$ is the terminal $\RealUp$ seal reached only after the topology, compact-metric, derived-point, window, and readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for $T,K,D,W,R,E$ and for the structural replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay of every perfect-set consumer request through
$$
T,K,D,W,R \longmapsto E \longmapsto H,C,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\PerfectSetUp$, $\TopologyUp$, $\CompactMetricUp$, $\RealUp$, $\CantorBendixsonUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PerfectSetUp}$ row.
\end{enumerate}
The carrier has no coordinate for a selected countable dense subset, transfinite rank, isolated-point enumeration, quotient equality of real names, host closed-set equality, countable choice, or ambient compactness beyond the displayed rows.
\end{definition}

\begin{theorem}[PerfectSet NameCert obligations]
\label{thm:perfect-set-namecert-obligations}
For every accepted $\PerfectSetUp$ carrier $S=(T,K,D,W,R,E,H,C,P,N)$, the local $\NameCert_{\PerfectSetUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the topology, compact-metric, derived-point, finite-window, regular readback, Real-seal, transport, replay, provenance, and local naming rows;
\item closed-set exposure, requiring complement and neighborhood requests to pass through the topology row $T$ and compact-metric row $K$;
\item derived-point non-isolation, requiring each displayed point-and-neighborhood request to receive its second compatible point through $D$ at a window listed in $W$;
\item real-seal compatibility, requiring every metric comparison and non-isolation witness to pass through $R$ before the terminal seal $E$ is consumed;
\item ledger nonescape, requiring $H,C,P,N$ to export no isolated-point selector, transfinite derivative rank, quotient real equality, host closed-set equality, countable-choice schedule, or ambient completeness theorem.
\end{enumerate}
No perfect-set obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier $S=(T,K,D,W,R,E,H,C,P,N)$. Carrier admission exposes exactly the topology row, compact-metric source, derived-point ledger, finite window schedule, regular readback row, Real seal, and the structural rows.

Closed-set exposure is read through $T$ and $K$. The topology row supplies neighborhood and complement tests, while the compact-metric row supplies the finite metric inspection data used by the same requests.

The derived-point clause is the row $D$. For each displayed point-and-neighborhood request, the finite window row $W$ names the inspected neighborhood and $D$ records the compatible second point before any Real-facing seal is available.

Finally, $R$ and $E$ bind the metric and Real-facing parts of the route, while $H,C,P,N$ transport, replay, source, and name the same packet. Since the excluded classical data are not carrier coordinates, the five listed rows exhaust the local certificate.
\end{proof}

\begin{theorem}[PerfectSet derived-point nonescape]
\label{thm:perfect-set-derived-point-nonescape}
Every $\CantorBendixsonUp$ or $\RealUp$ consumer of an accepted $\PerfectSetUp$ packet must read the topology row, compact-metric row, derived-point ledger, finite window schedule, regular readback route, and terminal Real seal before treating the set as a perfect kernel. In particular, the consumer receives the finite route
$$
T,K,D,W,R \longmapsto E \longmapsto H,C,P,N
$$
and receives no isolated-point selector, transfinite derivative rank, quotient real equality, host closed-set equality, countable-choice schedule, or ambient compactness theorem outside the displayed certificate.
\end{theorem}
\begin{proof}
Start with a consumer request for the perfect-kernel face. By \autoref{thm:perfect-set-namecert-obligations}, the request first passes through the topology and compact-metric rows $T,K$ and then through the derived-point ledger $D$ at a finite window listed in $W$.

The regular readback row $R$ and terminal seal $E$ are the only Real-facing route in the carrier. Thus a Cantor-Bendixson consumer can consume this packet only as the retained perfect-set face displayed by \autoref{ch:concrete-instances-cantor-bendixson-namecert}.

The structural rows $H,C,P,N$ preserve and replay the same route. Because the carrier lacks coordinates for isolated-point selection, transfinite ranks, quotient equality, host closed-set equality, countable choice, or extra compactness principles, no such data can escape through the derived-point ledger.
\end{proof}

\closureat{PerfectSetUp}{seedStr}

\begin{closurestatus}{\PerfectSetUp}
  \constructivestory{A $\PerfectSetUp$ packet is generated from topology rows, compact-metric inspection rows, a derived-point ledger, finite request windows, regular rational readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:perfect-set-carrier}, \autoref{thm:perfect-set-namecert-obligations}, and \autoref{thm:perfect-set-derived-point-nonescape} seed the finite perfect-kernel certificate consumed by Cantor-Bendixson and Real-facing routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close transfinite Cantor-Bendixson decomposition, selected isolated-point enumeration, quotient real equality, host closed-set equality, countable choice, ambient compactness, Lean theorem coverage, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, closed-set exposure, derived-point non-isolation, Real-seal compatibility, ledger nonescape, and Cantor-Bendixson consumer routing for BEDC.Derived.PerfectSetUp.}
\end{closurestatus}
