\chapter{A Concrete Naming Certificate for $\BoxDimensionUp$}
\label{ch:concrete-instances-box-dimension-namecert}
\origin{human}

Following Falconer's finite-cover formulation of box dimension, the $\BoxDimensionUp$ packet records the BEDC surface at which metric scale, finite covers, and counting ledgers become an inspectable dimension invariant. It is downstream of the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the compact metric finite-net boundary of \autoref{ch:concrete-instances-compactmetric-namecert}, the refinement language of \autoref{ch:concrete-instances-coveringdimension-namecert}, and the rational dense route of \autoref{ch:concrete-instances-real-separability-namecert}. The chapter names the finite scale-cover data used by lower and upper box-dimension reads; it does not add Hausdorff measure, choice over optimal covers, host logarithms, quotient compacta, or a detached completion object.

\begin{definition}[Box dimension finite-cover carrier]
\label{def:box-dimension-carrier}
A $\BoxDimensionUp$ carrier over a compact metric source $X$ is a finite $\BHist$ packet
$$
B=(M,K,S,C,R,D,N,H,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the inherited $\MetricUp$ distance row on $X$, including the point classifier and the visible distance-witness ledger.
\item $K$ is the compact metric source row. It exposes the finite-net and complete-limit data from \autoref{ch:concrete-instances-compactmetric-namecert} before any scale cover is read.
\item $S$ is the dyadic scale row. Each accepted scale is a positive dyadic tolerance history, ordered by refinement toward smaller radii.
\item $C$ is the finite cover row. For each scale in $S$, it displays a finite family of balls whose centers are carried by $X$ and whose radii are bounded by the current dyadic scale.
\item $R$ is the refinement ledger. It records how a cover at a smaller dyadic scale refines the previous visible cover without selecting an optimal cover in the host theory.
\item $D$ is the counting and comparison ledger. It records the finite cardinality of each displayed cover and the rational bounds used by the lower and upper box-dimension comparison read.
\item $N$ is the separability net route. It allows the centers of the displayed finite covers to be read through the $\RealSeparabilityUp$ dense-window surface when the compact metric source is a real metric carrier.
\item $H$ stores componentwise $\hsame$ transport for metric points, dyadic scales, cover centers, cover membership, refinement rows, counting comparisons, and dense-route data.
\item $P$ is the $\Pkg$ provenance over $\BoxDimensionUp$, $\MetricUp$, $\CompactMetricUp$, $\CoveringDimensionUp$, $\RealSeparabilityUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\BoxDimensionUp}$ row.
\end{enumerate}
The carrier has no coordinate for a selected minimal cover, ambient Euclidean embedding, host logarithm, Hausdorff-measure comparison, quotient compactum, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Box dimension finite-cover obligations]
\label{thm:box-dimension-finite-cover-obligations}
For every accepted $\BoxDimensionUp$ carrier
$$
B=(M,K,S,C,R,D,N,H,P,L),
$$
the local $\NameCert_{\BoxDimensionUp}$ surface consists exactly of finite scale-cover obligations: carrier admission for the metric and compact rows, positive dyadic scale exposure, finite cover membership, radius comparison, refinement transport, cover-count comparison, separability-net routing when the source is Real-facing, provenance, and local naming. No obligation is stored outside $M,K,S,C,R,D,N,H,P,L$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:box-dimension-carrier}. The rows $M$ and $K$ provide the metric source and compact metric finite-net boundary, while $S$ provides the positive dyadic scales at which covers are inspected.

For a fixed scale, $C$ displays the finite cover as packet data: center histories, ball radii, membership rows, and radius bounds. The row $D$ counts that finite family and stores the rational comparisons used by lower and upper box-dimension reads.

When the scale is refined, $R$ is the only refinement witness. It transports a visible cover to a smaller visible cover through the recorded refinement ledger rather than by selecting a host-minimal cover.

The dense-source route $N$, the transport row $H$, the provenance row $P$, and the naming row $L$ preserve the same finite data. Since the carrier contains no coordinate for optimal cover selection, host logarithms, Hausdorff measure, quotient compacta, Lean verification, or bridge checking, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Box dimension covering-dimension anchor]
\label{thm:box-dimension-covering-dimension-anchor}
Every $\CoveringDimensionUp$ consumer of an accepted $\BoxDimensionUp$ packet may read only the displayed finite cover and refinement rows $C$ and $R$ after the compact metric source $K$ and dyadic scale row $S$ have been exposed. The anchor sends scale-cover covers to covering-dimension refinement ledgers as finite packet data; it does not export a minimal cover, a Lebesgue-number principle, a Hausdorff-measure estimate, or an ambient Euclidean coordinate system.
\end{theorem}
\begin{proof}
Start with the accepted carrier $B=(M,K,S,C,R,D,N,H,P,L)$. The compact metric row $K$ is read before scale-cover data, so the consumer begins with the same finite-net and complete-limit boundary used by the compact metric certificate.

Expose a dyadic scale through $S$ and the corresponding finite cover through $C$. These rows provide exactly the cover families, centers, radius bounds, and membership witnesses that a covering-dimension refinement argument may inspect.

Route the handoff through $R$. The refinement ledger records how smaller-scale covers refine the displayed cover family, matching the finite-cover language of \autoref{ch:concrete-instances-coveringdimension-namecert} without introducing a host-selected optimal cover.

The counting row $D$ and structural rows $H,P,L$ remain bookkeeping for the same displayed covers. Because no row stores a Lebesgue-number theorem, Hausdorff-measure estimate, Euclidean embedding, or minimal-cover selector, the covering-dimension anchor is limited to the finite refinement surface.
\end{proof}

\begin{theorem}[Box dimension real-separability net route]
\label{thm:box-dimension-real-separability-net-route}
When the compact metric source of an accepted $\BoxDimensionUp$ packet is a Real-facing metric carrier, every scale-cover center read that reaches a $\RealSeparabilityUp$ consumer factors through the displayed route
$$
\DyadicRatCoreUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp \longrightarrow \RealSeparabilityUp
$$
before the center may be used as a dense-net witness. The route uses only the dyadic scale row $S$, finite cover row $C$, counting ledger $D$, separability route $N$, transport row $H$, provenance row $P$, and local name row $L$.
\end{theorem}
\begin{proof}
Project the box-dimension carrier. The row $S$ supplies the dyadic scale, and the row $C$ supplies the finite cover centers inspected at that scale.

Read those centers through the Real-facing dense route $N$. By \autoref{ch:concrete-instances-real-separability-namecert}, a separability consumer reaches Real data through dyadic tolerance, finite stream windows, regular rational readback, and the terminal Real seal before it may consume the local density surface.

The counting row $D$ travels with the same finite cover family, so the number of displayed centers is the finite count used by the scale-cover comparison. The transport and provenance rows $H,P,L$ preserve the route without adding a selected nearest point, host real equality, quotient stream, ambient completeness, or choice over balls.

Thus every Real-facing center read factors through $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\RealSeparabilityUp$ before it is available as dense-net evidence for the box-dimension packet.
\end{proof}

\begin{closurestatus}{\BoxDimensionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:box-dimension-carrier}, \autoref{thm:box-dimension-finite-cover-obligations}, \autoref{thm:box-dimension-covering-dimension-anchor}, and \autoref{thm:box-dimension-real-separability-net-route} seed the finite scale-cover route for compact metric carriers, covering-dimension refinement ledgers, and RealSeparability dense-net consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Hausdorff dimension, minimal-cover selection, host logarithm analysis, ambient Euclidean embeddings, quotient compacta, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic scale positivity, finite cover membership, refinement ledgers, cover-count comparison, and RealSeparability net routing for BEDC.Derived.BoxDimensionUp.}
  \constructivestory{A $\BoxDimensionUp$ packet is generated from a metric row, compact metric source row, dyadic scale row, finite cover row, refinement ledger, counting comparison ledger, separability net route, componentwise transport, provenance, and a local NameCert row.}
\end{closurestatus}
