\chapter{A Concrete Naming Certificate for $\DyadicClosedIntervalEndpointGridUp$}
\label{ch:concrete-instances-dyadic-closed-interval-endpoint-grid-namecert}
\origin{human}

Following Bishop and Bridges constructive interval analysis, the $\DyadicClosedIntervalEndpointGridUp$ packet records the finite dyadic endpoint grid read before compact-uniform-continuity interval consumers inspect nets, moduli, or coverage rows. It refines the closed bounded interval source of \autoref{ch:concrete-instances-closedboundedinterval-namecert} through the dyadic interval surface of \autoref{ch:concrete-instances-dyadicinterval-namecert}, the StreamName and RegSeqRat readback rows, and the terminal Real seal. The route serves the compact-uniform-continuity program of \autoref{ch:visions-compact-uniform-continuity} without invoking open-cover compactness, selected subcovers, quotient real equality, trichotomy, or ambient completeness.

\begin{definition}[Dyadic closed interval endpoint-grid carrier]
\label{def:dyadic-closed-interval-endpoint-grid-carrier}
A $\DyadicClosedIntervalEndpointGridUp$ carrier is a finite $\BHist$ packet
$$
G=(I,D,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the source $\ClosedBoundedIntervalUp$ row, exposing lower endpoint, upper endpoint, endpoint order, rational containment, dyadic containment, StreamName windows, RegSeqRat readbacks, and the Real seal through the root package.
\item $D$ is the finite $\DyadicIntervalUp$ endpoint-grid row, listing dyadic cells whose endpoints are admitted by the interval source and ordered by the same endpoint-order route.
\item $W$ is the finite window row, exposing the StreamName windows attached to the grid cells before any net, modulus, or coverage consumer reads them.
\item $R$ is the $\RegSeqRatUp$ readback row for the displayed dyadic endpoints and cell windows.
\item $E$ is the terminal $\RealUp$ seal row, reached only after $I,D,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport across the closed interval source, dyadic grid, windows, RegSeqRat readbacks, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from compact-uniform-continuity interval requests through the endpoint grid before finite-net or modulus rows are inspected.
\item $P$ is the $\Pkg$ provenance over $\ClosedBoundedIntervalUp$, $\DyadicIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, compact-uniform-continuity interval consumers, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicClosedIntervalEndpointGridUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through $I,D,W,R,E,H,C,P,N$. It has no coordinate for host closed intervals, open-cover compactness, selected subcovers, selected points, quotient real equality, trichotomy, choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Dyadic closed interval endpoint-grid obligations]
\label{thm:dyadic-closed-interval-endpoint-grid-obligations}
For every accepted $\DyadicClosedIntervalEndpointGridUp$ carrier $G=(I,D,W,R,E,H,C,P,N)$, the local $\NameCert_{\DyadicClosedIntervalEndpointGridUp}$ surface consists of carrier admission, dyadic-cell exposure, endpoint-order preservation, window handoff, Real-seal nonescape, and local naming. The carrier admits only source rows from $\ClosedBoundedIntervalUp$, exposes dyadic cells only through $D$, preserves endpoint order from $I$ to every displayed cell endpoint, hands StreamName windows and RegSeqRat readbacks through $W,R$, reaches the Real seal only through $E$, and names the entire route by $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-closed-interval-endpoint-grid-carrier}. The source row $I$ is the only closed bounded interval input, and the finite grid row $D$ is the only coordinate listing dyadic endpoint cells.

Endpoint order is inherited from the source row before any grid cell is read. Since $D$ is attached to $I$, every displayed dyadic endpoint is admitted through the same lower-endpoint, upper-endpoint, order, rational-containment, and dyadic-containment route used by \autoref{ch:concrete-instances-closedboundedinterval-namecert}.

The consumer-facing rows are then forced through $W,R,E$. StreamName windows are exposed by $W$, regular rational endpoint readbacks by $R$, and the terminal Real seal by $E$. None of those rows supplies host compactness data or a selected subcover.

Finally $H,C,P,N$ transport, replay, source, and name exactly this displayed route. Because the carrier has no other coordinate, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Dyadic closed interval endpoint-grid window handoff]
\label{thm:dyadic-closed-interval-endpoint-grid-window-handoff}
Every compact-uniform-continuity interval read that consumes an accepted $\DyadicClosedIntervalEndpointGridUp$ carrier must pass through the displayed endpoint grid
$$
\ClosedBoundedIntervalUp \longmapsto \DyadicIntervalUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
before it reads any finite-net row, coverage row, pointwise-modulus row, uniform-modulus row, or compactness consumer row.
\end{theorem}
\begin{proof}
Start with the accepted carrier $G=(I,D,W,R,E,H,C,P,N)$. A compact-uniform-continuity interval consumer first receives $I$, so the closed bounded interval endpoint and containment package is displayed before any grid row is available.

The read then passes through the finite dyadic endpoint grid $D$. This row exposes the dyadic cells and their endpoint order, but it does not yet expose a finite net, a cover, or a modulus.

Next the consumer receives the window and readback rows $W,R,E$. These rows hand off StreamName windows, RegSeqRat endpoint readbacks, and the Real seal as finite endpoint-grid data.

Only after this route has been replayed by $C$ and sourced by $P$ may a downstream compact-uniform-continuity consumer add net or modulus rows. Thus the interval read reaches the compact-uniform-continuity surface through the endpoint grid rather than through an open-cover compactness principle or a host real interval.
\end{proof}

\falsifiablePrediction{An accepted compact-uniform-continuity interval consumer that reads finite-net, coverage, pointwise-modulus, uniform-modulus, or compactness rows before inspecting $I,D,W,R,E,H,C,P,N$ is outside the $\DyadicClosedIntervalEndpointGridUp$ packet.}

\independenceWitness{closedboundedinterval, dyadicinterval, streamname, regseqrat, real: $\DyadicClosedIntervalEndpointGridUp$ is not bijective to any listed sibling because it jointly carries the closed bounded interval root package, a finite dyadic endpoint grid, finite windows, regular rational readbacks, a terminal Real seal, transport, replay, provenance, and local naming for compact-uniform-continuity interval consumers.}

\closureat{DyadicClosedIntervalEndpointGridUp}{seedStr}

\begin{closurestatus}{\DyadicClosedIntervalEndpointGridUp}
  \constructivestory{A $\DyadicClosedIntervalEndpointGridUp$ packet is generated from a ClosedBoundedInterval source row, DyadicInterval endpoint-grid row, StreamName window row, RegSeqRat readback row, Real seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-closed-interval-endpoint-grid-carrier}, \autoref{thm:dyadic-closed-interval-endpoint-grid-obligations}, and \autoref{thm:dyadic-closed-interval-endpoint-grid-window-handoff} seed the finite endpoint-grid route for compact-uniform-continuity interval consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, finite-net compactness, open-cover compactness, pointwise-modulus extraction, uniform-modulus construction, quotient real equality, trichotomy, selected points, selected subcovers, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic-cell exposure, endpoint-order preservation, window handoff, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.DyadicClosedIntervalEndpointGridUp.}
\end{closurestatus}
