\chapter{A Concrete Naming Certificate for $\CauchyStructureUp$}
\label{ch:concrete-instances-cauchy-structure-namecert}
\origin{human}

Following Bourbaki and Kelley on Cauchy structures and Bishop--Bridges on constructive completion, the $\CauchyStructureUp$ packet names the finite criterion surface where Cauchy filters and Cauchy nets are read through stream windows, regular rational readback, dyadic tolerances, and a terminal real seal. It is grounded in the StreamName route of \autoref{ch:concrete-instances-streamname-namecert}, the regular sequence route of \autoref{ch:concrete-instances-regseqrat-namecert}, the real seal of \autoref{ch:concrete-instances-real-namecert}, the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the Cauchy-net surface of \autoref{ch:concrete-instances-cauchynet-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}.

\begin{definition}[Cauchy structure carrier]
\label{def:cauchy-structure-carrier}
A $\CauchyStructureUp$ carrier is a finite $\BHist$ packet
$$
K=(F,G,D,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the filter-base request row naming the finite family of Cauchy-filter requests accepted from \autoref{ch:concrete-instances-cauchyfilter-namecert};
\item $G$ is the net-directed request row naming the finite family of directed Cauchy-net requests accepted from \autoref{ch:concrete-instances-cauchynet-namecert};
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by both filter-base and net-directed requests;
\item $S$ is the finite $\StreamNameUp$ window inspected by every request before regular readback;
\item $R$ is the $\RegSeqRatUp$ readback row attached to the stream window and dyadic ledger;
\item $E$ is the terminal $\RealUp$ seal reached by the displayed readback route;
\item $H$ is componentwise $\hsame$ transport across $F,G,D,S,R,E$;
\item $C$ is displayed $\Cont$ replay from each filter-base or net-directed request through $D,S,R,E$;
\item $P$ is $\Pkg$ provenance over $\CauchyFilterUp$, $\CauchyNetUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\CauchyStructureUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient filters, selected limits, countable choice, trichotomy, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Cauchy structure NameCert obligations]
\label{thm:cauchy-structure-namecert-obligations}
For the carrier of \autoref{def:cauchy-structure-carrier}, the local $\NameCert_{\CauchyStructureUp}$ surface consists exactly of carrier admission for $K=(F,G,D,S,R,E,H,C,P,N)$, filter-base request exposure through $F$, net-directed request exposure through $G$, dyadic tolerance exposure through $D$, finite StreamName window exposure through $S$, RegSeqRat readback through $R$, Real seal handoff through $E$, transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier row by row. The filter-base and net-directed requests are the two input faces, and both are read only through the same dyadic tolerance ledger, StreamName window, regular rational readback, and Real seal route.

Transport and replay are structural rows. The transport row compares the displayed request, tolerance, window, readback, and seal coordinates componentwise; the replay row orders every request through $D,S,R,E$ before a consumer may read the result.

The package provenance and local NameCert row name exactly this finite packet. Since the carrier contains no other coordinate, the listed rows are precisely the NameCert obligations.
\end{proof}

\begin{theorem}[Cauchy structure filter-net criterion]
\label{thm:cauchy-structure-filter-net-criterion}
Every accepted $\CauchyStructureUp$ route orders filter-base and net-directed Cauchy reads through the same finite criterion sequence
$$
F,G \longmapsto D \longmapsto S \longmapsto R \longmapsto E.
$$
A filter-facing consumer and a net-facing consumer therefore meet at the displayed dyadic tolerance ledger, StreamName window, RegSeqRat readback, and Real seal; neither route may replace that finite sequence by quotient filters, selected limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
For the filter direction, project the $F$ row and follow its replay row. The replay first opens the dyadic tolerance ledger $D$, then the finite StreamName window $S$, then the RegSeqRat readback $R$, and only then the Real seal $E$.

For the net direction, project the $G$ row and use the same replay ordering. Directed requests may change the source face, but they do not introduce a new tolerance, window, readback, or seal coordinate outside $D,S,R,E$.

The componentwise transport row $H$ identifies admissible changes only along the displayed coordinates, while $P$ and $N$ record provenance and local naming. Thus the common filter-net criterion is the finite route above, with no quotient, choice, trichotomy, selected-limit, or ambient-completeness bypass.
\end{proof}

\closureat{CauchyStructureUp}{seedStr}

\begin{closurestatus}{\CauchyStructureUp}
  \constructivestory{A $\CauchyStructureUp$ packet is generated from filter-base requests, net-directed requests, dyadic tolerance rows, finite StreamName windows, RegSeqRat readback, a RealUp seal, componentwise transport, displayed replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-structure-carrier}, \autoref{thm:cauchy-structure-namecert-obligations}, and \autoref{thm:cauchy-structure-filter-net-criterion} bind the finite L10 criterion surface connecting Cauchy filters and Cauchy nets to StreamName, RegSeqRat, DyadicRatCore, and RealUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected limits, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, request exposure, finite route ordering, and consumer nonescape for BEDC.Derived.CauchyStructureUp.}
\end{closurestatus}
