\chapter{A Concrete Naming Certificate for $\RiemannLebesgueLemmaUp$}
\label{ch:concrete-instances-riemann-lebesgue-lemma-namecert}
\origin{human}

Following Zygmund, Katznelson, and Folland on Fourier analysis, the $\RiemannLebesgueLemmaUp$ packet records the finite oscillatory-decay surface of the Riemann--Lebesgue lemma as BEDC NameCert data. It sits over the Fourier coefficient interface of \autoref{ch:concrete-instances-fourier-namecert}, the circle phase sampler of \autoref{ch:concrete-instances-s1-namecert}, the integral normalization route of \autoref{ch:concrete-instances-integral-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, and the averaging comparison supplied by \autoref{ch:concrete-instances-fejer-kernel-namecert}. The packet exposes finite coefficient windows and oscillatory handoff data; it does not import Haar measure, host $L^{1}$ theory, quotient function equality, general Fourier convergence, or ambient $\RealUp$ completeness.

\begin{definition}[Riemann--Lebesgue lemma carrier]
\label{def:riemann-lebesgue-lemma-carrier}
A $\RiemannLebesgueLemmaUp$ carrier is a finite $\BHist$ packet
$$
R=(F,S,I,W,T,A,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite $\FourierUp$ coefficient-window row, naming exactly the inspected frequency indices and coefficient requests.
\item $S$ is the $\SOneUp$ phase-sample row, recording the finite circle phases used to test the requested oscillations.
\item $I$ is the $\IntegralUp$ normalization and readback row, exposing only the finite integral observations used to form each coefficient.
\item $W$ is the window ledger pairing frequency indices, phase samples, and integral cells before any decay read is made.
\item $T$ is the $\RegSeqRatUp$ tolerance row, listing the rational error budgets attached to the coefficient windows.
\item $A$ is the finite averaging comparison row, allowed to cite the $\FejerKernelUp$ sibling only as a displayed smoothing comparison.
\item $Q$ is the oscillatory-decay handoff row, recording which finite tails have coefficient magnitude below the displayed tolerance.
\item $E$ is the terminal $\RealUp$ seal for coefficient values, tolerance comparisons, and accepted decay reads.
\item $H$ records componentwise $\hsame$ transport for the coefficient, phase, integral, window, tolerance, averaging, decay, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Fourier-coefficient request through $F,S,I,W,T,A,Q,E,H$.
\item $P$ is the $\Pkg$ provenance over $\RiemannLebesgueLemmaUp$, $\FourierUp$, $\SOneUp$, $\IntegralUp$, $\RegSeqRatUp$, $\RealUp$, $\FejerKernelUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RiemannLebesgueLemmaUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,S,I,W,T,A,Q,E,H,C,P,N$. It has no coordinate for Haar measure, host $L^{1}$ spaces, quotient equality of functions, a theorem of general Fourier convergence, selected representatives, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Riemann--Lebesgue lemma NameCert obligations]
\label{thm:riemann-lebesgue-lemma-namecert-obligations}
For every accepted $\RiemannLebesgueLemmaUp$ carrier
$$
R=(F,S,I,W,T,A,Q,E,H,C,P,N),
$$
the local $\NameCert_{\RiemannLebesgueLemmaUp}$ surface consists exactly of Fourier coefficient-window admission through $F$, circle phase-sample admission through $S$, integral normalization and readback through $I$, window and tolerance exposure through $W,T$, finite averaging comparison through $A$, oscillatory-decay handoff through $Q$, terminal real sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:riemann-lebesgue-lemma-carrier}. The rows $F,S,I$ expose the coefficient request, the finite phase samples, and the integral normalization before the packet can state any decay handoff.

The rows $W,T,A,Q$ supply the finite analytic body of the certificate. The window row pairs frequencies with inspected cells, the tolerance row records the rational budgets, the averaging row gives the displayed Fejer-kernel comparison, and the handoff row records exactly the tails accepted below those budgets.

The structural rows $E,H,C,P,N$ seal, transport, replay, source, and name the same data. Since the carrier has no coordinate for Haar measure, host $L^{1}$ theory, quotient function equality, general Fourier convergence, selected representatives, or ambient real completeness, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Riemann--Lebesgue oscillatory handoff]
\label{thm:riemann-lebesgue-lemma-oscillatory-handoff}
Every Fourier-decay consumer of an accepted $\RiemannLebesgueLemmaUp$ carrier factors through the displayed route
$$
\FourierUp \longmapsto \SOneUp \longmapsto \IntegralUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The optional $\FejerKernelUp$ comparison can be read only through the finite averaging row $A$, and the final decay read can inspect only $F,S,I,W,T,A,Q,E,H,C,P,N$. Thus the packet supplies a finite oscillatory-decay dependency for later Fourier approximation chapters without exporting Haar measure, host $L^{1}$ integration, quotient function equality, general convergence of Fourier series, or ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Begin with a Fourier-decay request. Carrier projection exposes $F$, so the consumer receives a finite coefficient window rather than an infinite Fourier transform.

The request next reads $S,I,W,T$. These rows bind each requested frequency to displayed circle phases, integral cells, window ledgers, and regular rational tolerances.

Only then can the consumer inspect $A,Q,E,H,C,P,N$. The averaging comparison remains a finite sibling comparison, the decay handoff is recorded at the displayed tolerances, and the real seal closes the numeric read. No excluded analytic object has a coordinate in the packet, so the handoff is exactly the displayed finite route.
\end{proof}

\falsifiablePrediction{An accepted $\RiemannLebesgueLemmaUp$ packet is refuted if a Fourier-decay consumer preserves the coefficient window while bypassing the displayed $\SOneUp$ phase samples, $\IntegralUp$ normalization row, $\RegSeqRatUp$ tolerance row, and terminal $\RealUp$ seal.}

\independenceWitness{fourier, sone, integral, regseqrat, real, fejer-kernel: none is bijective to $\RiemannLebesgueLemmaUp$ because the packet jointly carries coefficient windows, phase samples, integral normalization, tolerance ledgers, averaging comparison, oscillatory-decay handoff, transport, replay, provenance, and local NameCert rows.}

\closureat{RiemannLebesgueLemmaUp}{seedStr}

\begin{closurestatus}{\RiemannLebesgueLemmaUp}
  \constructivestory{A $\RiemannLebesgueLemmaUp$ packet is generated from finite Fourier coefficient windows, SOne phase samples, Integral normalization and readback rows, RegSeqRat tolerance rows, a finite FejerKernel comparison, an oscillatory handoff row, RealUp seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riemann-lebesgue-lemma-carrier}, \autoref{thm:riemann-lebesgue-lemma-namecert-obligations}, and \autoref{thm:riemann-lebesgue-lemma-oscillatory-handoff} seed the finite oscillatory-decay route over Fourier, circle phase, integral, regular rational, real-seal, and averaging rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Haar measure, host $L^{1}$ theory, quotient function equality, general Fourier convergence, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked coefficient-window admission, phase-sample exposure, integral normalization, tolerance exactness, finite averaging comparison, oscillatory handoff, real seal exposure, transport, replay, provenance, and local naming for BEDC.Derived.RiemannLebesgueLemmaUp.}
\end{closurestatus}
