\chapter{A Concrete Naming Certificate for $\CauchyLocatedApartnessUp$}
\label{ch:concrete-instances-cauchy-located-apartness-namecert}
\origin{human}

Following Bishop and Bridges, the $\CauchyLocatedApartnessUp$ packet records the constructive boundary where finite locator requests for a Cauchy real become positive located-apartness evidence. It consumes the Cauchy locator route of \autoref{ch:concrete-instances-cauchy-real-locator-namecert}, the located-apartness surface of \autoref{ch:concrete-instances-located-apartness-namecert}, the apartness-real interface of \autoref{ch:concrete-instances-apartnessreal-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. Its finite naming spine is read through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-dyadicratcore-namecert}.

The packet is a local handoff surface. It exports locator rows, endpoint-gap rows, finite stream windows, regular-rational readbacks, dyadic tolerance ledgers, real seals, transport rows, continuation replay, provenance, and a local NameCert row. It exports no trichotomy, no quotient real equality, no selected limit, no countable choice, no open-cover compactness, and no ambient $\RealUp$ completeness theorem.

\begin{definition}[Cauchy located-apartness carrier]
\label{def:cauchy-located-apartness-carrier}
A $\CauchyLocatedApartnessUp$ carrier is a finite $\BHist$ packet
$$
L=(Q,A,B,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\CauchyRealLocatorUp$ row answering finite rational locator requests for the Cauchy real being inspected.
\item $A$ and $B$ are endpoint-gap rows read through $\LocatedApartnessUp$ and $\ApartnessRealUp$, recording positive separation windows on the two sides of the located comparison.
\item $S$ is the finite $\StreamNameUp$ window ledger used to schedule the locator observations.
\item $R$ is the $\RegSeqRatUp$ readback row that turns the displayed stream windows into regular rational observations.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, including the radius and endpoint arithmetic used by the locator and apartness rows.
\item $E$ is the $\RealUp$ seal row reached only after $Q,A,B,S,R,D$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for locator rows, endpoint-gap rows, finite windows, readbacks, tolerance ledgers, real seals, continuation replay, provenance, and local naming.
\item $C$ stores displayed $\Cont$ replay from locator requests through stream windows, regular-rational readbacks, dyadic tolerance checks, endpoint-gap rows, and the final real seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyLocatedApartnessUp$, $\CauchyRealLocatorUp$, $\LocatedApartnessUp$, $\ApartnessRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyLocatedApartnessUp}$ row.
\end{enumerate}
The carrier has no coordinate for trichotomy, quotient real equality, selected limits, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy located-apartness NameCert obligations]
\label{thm:cauchy-located-apartness-namecert-obligations}
For every accepted $\CauchyLocatedApartnessUp$ carrier $L=(Q,A,B,S,R,D,E,H,C,P,N)$, the local $\NameCert_{\CauchyLocatedApartnessUp}$ surface consists exactly of carrier admission for the displayed rows, locator-window compatibility, endpoint-gap exactness, dyadic-tolerance coverage, real-seal handoff, transport replay, and non-escape from the finite route
$$
Q,S,R,D\longmapsto A,B\longmapsto E
$$
together with $H,C,P,N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-located-apartness-carrier}. The accepted tuple exposes the Cauchy locator row, two endpoint-gap rows, stream windows, regular-rational readback, dyadic tolerance ledger, real seal, transport, replay, provenance, and local naming.

Locator-window compatibility reads $Q$ only through $S,R,D$. A finite comparison request must display the scheduled stream window, its regular rational readback, and the tolerance ledger before any located-apartness row can be consumed.

Endpoint-gap exactness is supplied by $A$ and $B$. These rows carry the positive located-apartness evidence, while the real seal $E$ is downstream of the same locator and tolerance route.

Finally, $H,C,P,N$ preserve and name the route. Since the carrier contains no trichotomy, quotient equality, selected limit, countable-choice schedule, open-cover compactness theorem, or ambient real-completeness coordinate, the displayed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy locator to apartness handoff]
\label{thm:cauchy-located-apartness-locator-apartness-handoff}
Every accepted $\CauchyLocatedApartnessUp$ carrier converts a finite $\CauchyRealLocatorUp$ request into positive $\LocatedApartnessUp$ and $\ApartnessRealUp$ endpoint-gap evidence only through the displayed route
$$
Q\longmapsto S\longmapsto R\longmapsto D\longmapsto A,B\longmapsto E .
$$
Thus a downstream Real-facing comparison consumer receives a finite locator-apartness handoff, not trichotomy, quotient real equality, a selected limit, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a finite locator request in $Q$. The carrier forces the request to replay through the scheduled $\StreamNameUp$ window $S$, the $\RegSeqRatUp$ readback $R$, and the $\DyadicRatCoreUp$ tolerance ledger $D$.

Only after that route is displayed may the endpoint-gap rows $A$ and $B$ be read as located-apartness evidence. The $\RealUp$ seal $E$ records that the same finite route reaches the real-facing surface.

The structural rows $H,C,P,N$ transport, replay, package, and name exactly these coordinates. No excluded principle is a field of the carrier, so the handoff is exhausted by the finite locator, window, readback, tolerance, apartness, and seal rows.
\end{proof}

\begin{closurestatus}{\CauchyLocatedApartnessUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-located-apartness-carrier}, \autoref{thm:cauchy-located-apartness-namecert-obligations}, and \autoref{thm:cauchy-located-apartness-locator-apartness-handoff} seed the finite Cauchy locator to located-apartness boundary over stream windows, regular-rational readbacks, dyadic tolerance ledgers, endpoint-gap rows, Real seals, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim trichotomy, quotient real equality, selected limits, countable choice, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, locator-window compatibility, endpoint-gap exactness, dyadic-tolerance coverage, real-seal handoff, transport replay, and non-escape for BEDC.Derived.CauchyLocatedApartnessUp.}
  \constructivestory{A $\CauchyLocatedApartnessUp$ packet is generated from a CauchyRealLocator request row, LocatedApartness and ApartnessReal endpoint-gap rows, finite StreamName windows, RegSeqRat readbacks, DyadicRatCore tolerance ledgers, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
