\chapter{A Concrete Naming Certificate for $\HyperbolicVisualMetricUp$}
\label{ch:concrete-instances-hyperbolic-visual-metric-namecert}
\origin{ai}

The $\HyperbolicVisualMetricUp$ packet realizes the disk readout branch of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits after the Poincare disk metric surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the boundary-geodesic route of \autoref{ch:concrete-instances-hyperbolic-geodesic-boundary-namecert}, the boundary-shadow packet of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, and the boundary-fixed transport surface of \autoref{ch:concrete-instances-poincare-boundary-fixed-transport-namecert}. The packet names a simultaneous visual-metric read over displayed disk, metric, boundary, shadow, transport, and provenance rows; it does not turn the observer boundary into an object-level $\mathsf{T}$ or a completed global geometry.

\begin{definition}[Hyperbolic visual metric carrier]
\label{def:hyperbolic-visual-metric-carrier}
A $\HyperbolicVisualMetricUp$ carrier is a finite $\BHist$ packet
$$
V=(D,M,B,S,T,F,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the disk source row, read through the Poincare disk and unit-disk coordinate surface;
\item $M$ is the $\HyperbolicMetricUp$ metric-read row over the same disk source;
\item $B$ is the $\HyperbolicGeodesicBoundaryUp$ boundary row for geodesic far-end incidence;
\item $S$ is the $\HyperbolicBoundaryShadowUp$ shadow row attached to the displayed boundary read;
\item $T$ is the $\PoincareBoundaryFixedTransportUp$ classifier-preserving boundary transport row;
\item $F$ is the global-geometry refusal row, rejecting reads that replace displayed disk, metric, boundary, shadow, and transport rows by an object-level geometry;
\item $A$ is the vision anchor row tying the packet to the observer-expansion reading of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion};
\item $H$ records componentwise $\hsame$ transport for disk source, metric read, boundary row, shadow row, transport row, refusal row, and anchor row;
\item $C$ records displayed $\Cont$ replay from disk source through metric read, boundary read, shadow, transport, refusal, and provenance;
\item $P$ records $\Pkg$ provenance over $\HyperbolicVisualMetricUp$, $\HyperbolicMetricUp$, $\HyperbolicGeodesicBoundaryUp$, $\HyperbolicBoundaryShadowUp$, $\PoincareBoundaryFixedTransportUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\HyperbolicVisualMetricUp}$ row.
\end{enumerate}
The carrier has no coordinate for a completed boundary compactification, object-level $\mathsf{T}$, physical horizon, global metric oracle, or quotient boundary equality.
\end{definition}

\begin{theorem}[Hyperbolic visual metric obligation surface]
\label{thm:hyperbolic-visual-metric-obligation-surface}
For the carrier of \autoref{def:hyperbolic-visual-metric-carrier}, the local $\NameCert_{\HyperbolicVisualMetricUp}$ surface consists exactly of disk source admission, hyperbolic metric read admission, geodesic-boundary read admission, boundary-shadow admission, classifier-preserving boundary transport, global-geometry refusal, vision-anchor provenance, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier rows. The disk source $D$, metric read $M$, boundary row $B$, shadow row $S$, and transport row $T$ are the only geometric data available to the packet.

Use the sibling surfaces in order. $\HyperbolicMetricUp$ supplies the metric read, $\HyperbolicGeodesicBoundaryUp$ supplies the boundary incidence route, $\HyperbolicBoundaryShadowUp$ supplies the shadow row, and $\PoincareBoundaryFixedTransportUp$ supplies classifier-preserving transport.

The refusal and structural rows finish the surface. The row $F$ refuses any read that bypasses the displayed siblings, while $A,H,C,P,N$ only anchor, transport, replay, source, and name the same finite route. Thus the listed rows exhaust the local certificate.
\end{proof}

\begin{theorem}[Hyperbolic visual metric global-geometry refusal]
\label{thm:hyperbolic-visual-metric-global-geometry-refusal}
A visual metric read of an accepted $\HyperbolicVisualMetricUp$ packet is refused unless the displayed route contains disk source, metric read, boundary row, boundary shadow, classifier-preserving transport, provenance, and the global-geometry refusal row. The packet cannot replace those rows by an object-level $\mathsf{T}$, completed boundary compactification, physical horizon, or global metric oracle.
\end{theorem}
\begin{proof}
Read the geometric rows first. The carrier exposes disk source $D$, hyperbolic metric row $M$, geodesic-boundary row $B$, boundary-shadow row $S$, and boundary-fixed transport row $T$ as separate finite fields.

Apply the obligation surface. By \autoref{thm:hyperbolic-visual-metric-obligation-surface}, a local NameCert read can inspect only those rows plus refusal, anchor, transport, replay, provenance, and local naming.

The excluded objects have no carrier coordinate. Since $F$ explicitly refuses global-geometry substitution and $H,C,P,N$ only preserve the displayed route, no accepted read can produce object-level $\mathsf{T}$, completed compactification, physical horizon, or a metric oracle outside the packet.
\end{proof}

\begin{theorem}[Hyperbolic visual metric sibling separation]
\label{thm:hyperbolic-visual-metric-sibling-separation}
The $\HyperbolicVisualMetricUp$ carrier is not bijective, row for row, with any one of $\HyperbolicMetricUp$, $\HyperbolicGeodesicBoundaryUp$, $\HyperbolicBoundaryShadowUp$, $\PoincareBoundaryFixedTransportUp$, or $\DynSystemUp$. A bijection preserving local NameCert obligations would have to preserve simultaneous disk readout, metric read, boundary incidence, shadow, boundary-fixed transport, refusal, provenance, transport, replay, and local naming, and no listed sibling carries that whole surface.
\end{theorem}
\begin{proof}
Compare first with $\HyperbolicMetricUp$. The metric sibling supplies a disk metric read, but it does not carry boundary-geodesic incidence, boundary shadow, boundary-fixed transport, and global-geometry refusal as simultaneous rows.

Compare next with $\HyperbolicGeodesicBoundaryUp$ and $\HyperbolicBoundaryShadowUp$. These siblings supply boundary incidence and shadow reads, while neither also owns the metric read, boundary-fixed transport, and visual refusal row.

Finally compare with $\PoincareBoundaryFixedTransportUp$ and $\DynSystemUp$. Transport and flow rows can move or evolve displayed data, but they are not the full visual metric packet. Since each sibling omits at least one of $D,M,B,S,T,F,A$, no row-preserving bijection can preserve the $\HyperbolicVisualMetricUp$ obligations.
\end{proof}

\falsifiablePrediction{A visual metric read is refused whenever the packet lacks disk source, metric read, boundary shadow, transport, and provenance rows.}

\independenceWitness{hyperbolic\_metric, hyperbolic\_geodesic\_boundary, hyperbolic\_boundary\_shadow, poincare\_boundary\_fixed\_transport, dynsystem: the visual metric packet carries the simultaneous readout route not bijective with any one sibling.}

The Lean TasteGate site for $\HyperbolicVisualMetricUp$ must provide explicit $\mathsf{Nontrivial}\ \HyperbolicVisualMetricUp$ and $\mathsf{FieldFaithful}\ \HyperbolicVisualMetricUp$ instances. These instances keep disk source, metric read, boundary row, shadow row, boundary-fixed transport, refusal, provenance, transport, replay, and local naming as distinguishable fields.

\closureat{HyperbolicVisualMetricUp}{seedStr}

\begin{closurestatus}{\HyperbolicVisualMetricUp}
  \constructivestory{A $\HyperbolicVisualMetricUp$ packet is generated from a disk source row, HyperbolicMetricUp metric read, HyperbolicGeodesicBoundaryUp boundary row, HyperbolicBoundaryShadowUp shadow row, PoincareBoundaryFixedTransportUp transport, global-geometry refusal, vision-anchor provenance, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-visual-metric-carrier}, \autoref{thm:hyperbolic-visual-metric-obligation-surface}, \autoref{thm:hyperbolic-visual-metric-global-geometry-refusal}, and \autoref{thm:hyperbolic-visual-metric-sibling-separation} seed the finite visual-metric route over disk, metric, boundary, shadow, transport, refusal, and provenance rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close object-level $\mathsf{T}$, completed boundary compactification, physical horizons, global metric oracles, quotient boundary equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, visual metric obligation routing, global-geometry refusal, sibling separation, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming.}
\end{closurestatus}
