\chapter{A Concrete Naming Certificate for $\BishopLocatedCompletionReflectorUp$}
\label{ch:concrete-instances-bishop-located-completion-reflector-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and located real analysis, the $\BishopLocatedCompletionReflectorUp$ packet records the reflector row that binds the located-real completion route of \autoref{ch:concrete-instances-bishop-located-real-completion-namecert} to the public completion-reflector surface of \autoref{ch:concrete-instances-cauchycompletionreflector-namecert}. It consumes the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the located-real row of \autoref{ch:concrete-instances-located-real-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a human-origin reflector for displayed located completion data; it is not quotient completion equality, a selected limit, countable choice, trichotomy, or ambient completeness.

\begin{definition}[Bishop located completion reflector carrier]
\label{def:bishop-located-completion-reflector-carrier}
A $\BishopLocatedCompletionReflectorUp$ carrier is a finite $\BHist$ packet
$$
K=(B,R,D,S,Q,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BishopLocatedRealCompletionUp$ row exposing the located-real completion carrier through dyadic tolerances, finite stream windows, regular rational readback, locatedness, and a terminal real seal.
\item $R$ is the $\CauchyCompletionReflectorUp$ row exposing unit, counit, idempotence, extension, reflection, and local real-name transport for the same completion-facing read.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used by both the located completion route and the reflector's local real-name transport.
\item $S$ is the $\StreamNameUp$ finite-window row inspected at those displayed tolerances.
\item $Q$ is the $\RegSeqRatUp$ regular rational readback row obtained from the same finite windows.
\item $L$ is the $\LocatedRealUp$ locatedness row attached to $Q$.
\item $E$ is the $\RealUp$ seal reached only after $B,R,D,S,Q,L$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the located completion row, reflector row, dyadic tolerance, stream-window, regular readback, locatedness, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-facing request through $B,R,D,S,Q,L,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopLocatedCompletionReflectorUp$, $\BishopLocatedRealCompletionUp$, $\CauchyCompletionReflectorUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopLocatedCompletionReflectorUp}$ row binding the displayed completion-reflector packet.
\end{enumerate}
The classifier on accepted packets compares only these rows under the displayed transport and replay data. It has no coordinate for quotient streams, selected representatives, host real equality, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop located completion reflector NameCert obligations]
\label{thm:bishop-located-completion-reflector-namecert-obligations}
For every accepted $\BishopLocatedCompletionReflectorUp$ carrier $K=(B,R,D,S,Q,L,E,H,C,P,N)$, the local $\NameCert_{\BishopLocatedCompletionReflectorUp}$ surface consists exactly of carrier admission, Bishop-located completion exposure, CauchyCompletionReflector exposure, DyadicRatCore tolerance exposure, StreamName finite-window exposure, RegSeqRat readback, LocatedReal locatedness exposure, Real seal handoff, componentwise transport, displayed continuation replay, package provenance, and local naming. Every reflector-facing consumer reads only the displayed route
$$
B,R\longmapsto D\longmapsto S\longmapsto Q\longmapsto L\longmapsto E\longmapsto H\longmapsto C\longmapsto P\longmapsto N .
$$
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-located-completion-reflector-carrier}. The only analytic rows are the located completion row, the public reflector row, the dyadic tolerance ledger, finite stream windows, regular rational readback, locatedness row, and Real seal.

Read the route in order. The row $B$ supplies the located completion side and the row $R$ supplies the reflector side. Their common finite route is then displayed through $D,S,Q,L,E$, so the reflector consumer cannot choose a second tolerance ledger, a host stream, or a selected real representative.

The structural rows $H,C,P,N$ transport, replay, source, and name that same route. Since quotient streams, selected limits, host equality, countable choice, trichotomy, compactness, and ambient completeness have no coordinate in the carrier, they cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[Bishop located completion reflector route]
\label{thm:bishop-located-completion-reflector-route}
Every $\BishopLocatedCompletionReflectorUp$ consumer that treats displayed located Cauchy data as a reflector object must pass through the sibling route of \autoref{ch:concrete-instances-bishop-located-real-completion-namecert} and the public reflector route of \autoref{ch:concrete-instances-cauchycompletionreflector-namecert}. The accepted packet exposes the reflector only as the finite carrier $B,R,D,S,Q,L,E,H,C,P,N$ and exports no quotient completion equality, selected host limit, countable-choice selector, trichotomy split, detached $\RealUp$ completeness theorem, or host real equality test.
\end{theorem}
\begin{proof}
Start with the NameCert obligations. They force any reflector-facing read to expose both the Bishop-located completion row $B$ and the CauchyCompletionReflector row $R$ before the terminal real seal is readable.

The shared analytic route is $D,S,Q,L,E$. The dyadic tolerance row fixes the finite request, the StreamName row opens the corresponding windows, the RegSeqRat row repacks those windows as regular rational data, the LocatedReal row supplies the lower--upper separation evidence, and the Real row seals the route.

The sibling chapters supply adjacent but not interchangeable packets. $\BishopLocatedRealCompletionUp$ gives the located completion side, and $\CauchyCompletionReflectorUp$ gives the public reflector side. The present carrier binds both with the common dyadic, stream, regular-rational, located-real, and real-seal rows, so no omitted sibling or host-level object can replace it.
\end{proof}

\falsifiablePrediction{A claimed $\BishopLocatedCompletionReflectorUp$ read that reaches the $\RealUp$ seal without first displaying both the $\BishopLocatedRealCompletionUp$ row and the $\CauchyCompletionReflectorUp$ row over the shared dyadic, stream, regular-rational, and located-real route refutes the carrier surface.}

\independenceWitness{bishop-located-real-completion, cauchycompletionreflector, dyadicratcore, streamname, regseqrat, locatedreal, real: no listed sibling is bijective to $\BishopLocatedCompletionReflectorUp$ because this packet binds the located completion row and public reflector row to one shared finite tolerance, window, readback, locatedness, real-seal, transport, replay, provenance, and local naming surface.}

\closureat{BishopLocatedCompletionReflectorUp}{seedStr}

\begin{closurestatus}{\BishopLocatedCompletionReflectorUp}
  \constructivestory{A $\BishopLocatedCompletionReflectorUp$ packet is generated from a BishopLocatedRealCompletion row, a CauchyCompletionReflector row, DyadicRatCore tolerances, StreamName finite windows, RegSeqRat readback, LocatedReal locatedness, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-located-completion-reflector-carrier}, \autoref{thm:bishop-located-completion-reflector-namecert-obligations}, and \autoref{thm:bishop-located-completion-reflector-route} seed the finite reflector route binding located completion and public completion reflection over the shared dyadic, stream, regular-rational, located-real, and real-seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, quotient completion equality, selected limits, countable choice, trichotomy, host real equality, open-cover compactness, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, located-completion exposure, reflector exposure, tolerance-window exactness, regular readback, locatedness handoff, RealUp seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopLocatedCompletionReflectorUp.}
\end{closurestatus}
