\chapter{A Concrete Naming Certificate for $\FilterCompletionUniversalPropertyUp$}
\label{ch:concrete-instances-filter-completion-universal-property-namecert}
\origin{human}

Following Kelley and Bishop--Bridges, the $\FilterCompletionUniversalPropertyUp$ packet records the finite universal-property surface for the L10 filter-completion route. It sits after the completion packet of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}, the convergence boundary of \autoref{ch:concrete-instances-cauchyfilterlimit-namecert}, the universal extension surface of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, and the uniform handoff of \autoref{ch:concrete-instances-uniformcompletion-namecert}. The packet names the extension and uniqueness rows that downstream completion consumers may cite without importing quotient filters, selected limits, host equality, countable choice, or ambient completeness.

\begin{definition}[Filter completion universal-property carrier]
\label{def:filter-completion-universal-property-carrier}
A $\FilterCompletionUniversalPropertyUp$ carrier is a finite $\BHist$ packet
$$
U=(C,L,E,Q,F,R,A,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the $\CauchyFilterCompletionUp$ completion route, already tying the accepted read to a displayed Cauchy filter, finite windows, dyadic tolerances, regular readback, and a terminal $\RealUp$ seal.
\item $L$ is the $\CauchyFilterLimitUp$ convergence row consumed only after the completion route $C$ has exposed its source-filter and readback rows.
\item $E$ is the $\CompletionUniversalPropertyUp$ extension-and-uniqueness row attached to the same filter-completion route.
\item $Q$ is the $\UniformCompletionUp$ handoff row read as provenance for uniform-facing consumers, not as a detached completion object.
\item $F$ is the $\RegSeqRatUp$ regular readback row supplied by the same finite windows and dyadic tolerance ledger.
\item $R$ is the $\RealUp$ seal reached through $C,L,F$ and used as the terminal filter-completion target.
\item $A$ is the extension-uniqueness ledger, comparing accepted extension rows over the same $C,L,E,Q,F,R$ surface by displayed $\hsame$ transport.
\item $H$ records componentwise $\hsame$ transport for the completion route, convergence row, universal-property row, uniform handoff, regular readback, Real seal, extension ledger, replay, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay of the route
$$
C,L,F,R \longmapsto E,Q,A,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\FilterCompletionUniversalPropertyUp$, $\CauchyFilterCompletionUp$, $\CauchyFilterLimitUp$, $\CompletionUniversalPropertyUp$, $\UniformCompletionUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FilterCompletionUniversalPropertyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $C,L,E,Q,F,R,A,H,K,P,N$. It has no coordinate for quotient filters, selected filter limits, host equality of filters or real names, countable-choice selectors, ambient completeness, or a completion object detached from the displayed filter route.
\end{definition}

\begin{theorem}[Filter completion universal-property NameCert obligations]
\label{thm:filter-completion-universal-property-namecert-obligations}
For every accepted $\FilterCompletionUniversalPropertyUp$ carrier $U=(C,L,E,Q,F,R,A,H,K,P,N)$, the local $\NameCert_{\FilterCompletionUniversalPropertyUp}$ surface consists exactly of carrier admission for the displayed tuple; filter-completion exposure through $C$; convergence exposure through $L$ after the source-filter route has been read; regular readback through $F$ and the terminal $\RealUp$ seal $R$; completion-universal extension through $E$; uniform provenance through $Q$; uniqueness comparison through $A$ over the same rows; componentwise transport through $H$; displayed replay through $K$; provenance through $P$; local naming through $N$; and ledger refusal for quotient filters, selected limits, host equality, countable choice, ambient completeness, and detached completion objects.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:filter-completion-universal-property-carrier}. The accepted packet exposes exactly the Cauchy-filter completion route, convergence row, universal-property row, uniform handoff, regular readback, Real seal, uniqueness ledger, transport, replay, provenance, and local name.

The filter route is finite. The completion row $C$ is read before the convergence row $L$, the regular readback $F$, and the seal $R$, so no consumer can begin from a selected filter limit or a quotient-filter representative.

The universal-property route is also finite. Rows $E,Q,A$ are read only after the same filter-completion and Real-seal data have been displayed, while $H,K,P,N$ transport, replay, source, and name that route. Since no excluded host-side coordinate appears in the carrier, these rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Filter completion universal-property extension uniqueness]
\label{thm:filter-completion-universal-property-extension-uniqueness}
Let $U=(C,L,E,Q,F,R,A,H,K,P,N)$ be an accepted $\FilterCompletionUniversalPropertyUp$ packet. Any two extension rows consumed through $U$ are compared only by the displayed uniqueness ledger $A$ over the common route
$$
C,L,F,R \longmapsto E,Q \longmapsto A,H,K,P,N .
$$
Thus extension uniqueness is available to completion-facing consumers only after the same Cauchy-filter completion row, convergence row, regular readback, Real seal, universal-property row, and uniform handoff have been displayed. It cannot be replaced by host function equality, quotient-filter equality, a selected limit, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with two extension reads from the accepted packet. The carrier has a single universal-property row $E$ and a single uniqueness ledger $A$ attached to the displayed filter-completion route.

Replay the continuation row $K$. Both extension reads must pass through $C,L,F,R$ before $E$ and $Q$ are available, so the comparison has the same source-filter, readback, convergence, and Real-seal data on both sides.

The ledger $A$ then compares the two rows by displayed $\hsame$ transport, and $H,P,N$ preserve and name the same comparison. The refused host equalities, quotient objects, selected limits, choice selectors, and completeness principles have no coordinate inside $U$.
\end{proof}

\begin{theorem}[Filter completion universal-property filter handoff]
\label{thm:filter-completion-universal-property-filter-handoff}
Every $\CauchyFilterCompletionUp$, $\CauchyFilterLimitUp$, $\CompletionUniversalPropertyUp$, or $\UniformCompletionUp$ consumer of an accepted $\FilterCompletionUniversalPropertyUp$ packet reads the same finite handoff
$$
C,L,F,R,E,Q,A,H,K,P,N .
$$
The handoff starts from the displayed Cauchy-filter completion row, reads the convergence boundary and regular readback before the terminal $\RealUp$ seal, and then exposes extension, uniqueness, uniform provenance, transport, replay, provenance, and local naming. No consumer may replace that handoff by a quotient filter, selected filter limit, host equality, countable-choice selector, ambient completeness theorem, or detached completion carrier.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its only completion source is $C$, its only convergence row is $L$, its only regular readback and terminal seal rows are $F$ and $R$, and its only universal-property and uniform-facing rows are $E$ and $Q$.

Use the NameCert obligations of \autoref{thm:filter-completion-universal-property-namecert-obligations}. They order the read from filter-completion exposure through convergence, readback, seal, extension, uniqueness, uniform provenance, transport, replay, package provenance, and local naming.

The sibling surfaces enforce the same boundary: \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert} supplies the completion source, \autoref{ch:concrete-instances-cauchyfilterlimit-namecert} supplies the convergence boundary, and \autoref{ch:concrete-instances-uniformcompletion-namecert} supplies only the uniform-facing provenance handoff. Since the carrier has no extra coordinate, the listed finite handoff is the whole exported route.
\end{proof}

\falsifiablePrediction{Every accepted $\FilterCompletionUniversalPropertyUp$ consumer that exports extension existence, extension uniqueness, filter convergence, or uniform-completion handoff while omitting one of the displayed Cauchy-filter completion, Cauchy-filter limit, regular readback, Real seal, completion-universal, uniform provenance, transport, replay, package provenance, or local naming rows refutes the packet.}

\independenceWitness{cauchyfiltercompletion, cauchyfilterlimit, completionuniversalproperty, uniformcompletion, regseqrat, real: none is bijective because $\FilterCompletionUniversalPropertyUp$ jointly carries filter-completion source, convergence boundary, regular readback, terminal Real seal, extension, uniqueness, uniform provenance, transport, replay, package provenance, and local NameCert rows in one universal-property packet.}

\closureat{FilterCompletionUniversalPropertyUp}{seedStr}

\begin{closurestatus}{\FilterCompletionUniversalPropertyUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:filter-completion-universal-property-carrier}, \autoref{thm:filter-completion-universal-property-namecert-obligations}, \autoref{thm:filter-completion-universal-property-extension-uniqueness}, and \autoref{thm:filter-completion-universal-property-filter-handoff} seed the finite L10 filter-completion universal-property route over Cauchy-filter completion, filter convergence, regular readback, Real seal, universal extension, uniform provenance, transport, replay, package provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, selected filter limits, host equality, countable choice, ambient completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, convergence exposure, extension uniqueness, filter handoff, uniform provenance, and non-escape proofs for BEDC.Derived.FilterCompletionUniversalPropertyUp.}
  \constructivestory{A $\FilterCompletionUniversalPropertyUp$ packet is generated from a CauchyFilterCompletion row, a CauchyFilterLimit convergence row, a CompletionUniversalProperty row, a UniformCompletion provenance row, a RegSeqRat readback, a RealUp seal, an extension-uniqueness ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
