\chapter{A Concrete Naming Certificate for $\CauchyWindowStabilityBridgeUp$}
\label{ch:concrete-instances-cauchy-window-stability-bridge-namecert}
\origin{human}

Following Bishop and Bridges, the $\CauchyWindowStabilityBridgeUp$ packet records the finite tail-window stability bridge used by the regular-Cauchy route of \autoref{ch:visions-real-completeness}. It sits after the finite window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The bridge names shared finite tail-window transport; it is not a hidden limit selector, quotient stream equality, host equality of real names, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy window stability bridge carrier]
\label{def:cauchy-window-stability-bridge-carrier}
A $\CauchyWindowStabilityBridgeUp$ carrier is a finite $\BHist$ packet
$$
B=(S_0,S_1,T,D,R_0,R_1,E_0,E_1,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S_0$ and $S_1$ are $\StreamNameUp$ finite-window rows for the two regular-Cauchy presentations being compared.
\item $T$ is the common finite tail-window row, listing the precision requests and indices beyond which the two presentations are read through the same displayed window schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the shared tail window and to every rational comparison used by the bridge.
\item $R_0$ and $R_1$ are $\RegSeqRatUp$ readback rows extracted from $S_0$ and $S_1$ at the tolerances named by $D$.
\item $E_0$ and $E_1$ are the visible $\RealUp$ seal rows reached only after the shared tail window, dyadic tolerance ledger, and regular rational readbacks have been displayed.
\item $H$ stores componentwise $\hsame$ transport for stream windows, the common tail row, dyadic tolerances, regular readbacks, Real seals, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from precision requests to common tail windows, from windows to regular readbacks, from dyadic tolerances to comparison rows, and from readbacks to the two Real seals.
\item $P$ is the $\Pkg$ provenance over $\CauchyWindowStabilityBridgeUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyWindowStabilityBridgeUp}$ row.
\end{enumerate}
The accepted carrier contains no selected limit, no quotient representative for streams, no host equality of real names, no countable-choice sequence, and no ambient completeness coordinate. It names only the finite common-tail bridge displayed by $T,D,R_0,R_1,E_0,E_1,H,C,P,N$.
\end{definition}

\begin{theorem}[Cauchy window stability bridge NameCert obligations]
\label{thm:cauchy-window-stability-bridge-namecert-obligations}
For an accepted carrier $B=(S_0,S_1,T,D,R_0,R_1,E_0,E_1,H,C,P,N)$, the local $\NameCert_{\CauchyWindowStabilityBridgeUp}$ obligations are exactly carrier admission; finite window exposure through $S_0$ and $S_1$; common tail-window admission through $T$; dyadic tolerance exactness through $D$; regular rational readback through $R_0$ and $R_1$; Real-seal admission through $E_0$ and $E_1$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $C$; $\Pkg$ provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier. The two stream rows $S_0,S_1$, the common tail row $T$, the dyadic ledger $D$, the readbacks $R_0,R_1$, and the seals $E_0,E_1$ are the entire analytic surface of the bridge.

The tail-window row is the only stability interface. It records which finite windows are shared for the precision request under consideration, while the dyadic ledger records the rational tolerance used to compare the two readbacks.

The structural rows add no hidden equality or limit object. Transport $H$, replay $C$, provenance $P$, and the local name $N$ preserve the displayed rows and expose no coordinate for quotient streams, selected limits, countable choice, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[Tail-window transport]
\label{thm:cauchy-window-stability-bridge-tail-transport}
Every stability read exported by an accepted $\CauchyWindowStabilityBridgeUp$ packet factors through the finite route
$$
S_0,S_1 \longmapsto T \longmapsto D \longmapsto R_0,R_1 \longmapsto E_0,E_1 \longmapsto H,C,P,N .
$$
Thus shared regular-Cauchy tail transport is determined by displayed $\StreamNameUp$ windows, one common finite tail row, $\DyadicRatCoreUp$ tolerances, $\RegSeqRatUp$ readbacks, and componentwise $\hsame$ replay.
\end{theorem}
\begin{proof}
Begin with the two finite stream rows. A stability consumer may inspect only the windows exposed by $S_0$ and $S_1$.

Read the common tail row next. The row $T$ names the shared finite window schedule for the current precision request, and the dyadic ledger $D$ attaches the tolerance used to compare the two regular rational readbacks.

The regular readbacks and seals are downstream. Rows $R_0,R_1$ are consumed before $E_0,E_1$, and the structural rows $H,C,P,N$ replay the same finite route. No selected tail, quotient stream, or countable-choice family is available outside this packet.
\end{proof}

\begin{theorem}[Real-seal stability handoff]
\label{thm:cauchy-window-stability-bridge-real-seal-handoff}
For every accepted $\CauchyWindowStabilityBridgeUp$ packet, the two $\RealUp$ seal rows $E_0$ and $E_1$ are accessible only after the shared tail-window row $T$, dyadic tolerance row $D$, and regular rational readbacks $R_0,R_1$ have been displayed. Consequently a Real-completion consumer that cites this bridge receives a finite seal-stability handoff, not a proof of ambient $\RealUp$ completeness or quotient equality of real names.
\end{theorem}
\begin{proof}
Project the carrier and isolate the seal coordinates. The rows $E_0,E_1$ occur only as terminal rows of the displayed bridge packet.

Apply the tail-window transport theorem. It forces every stability read through $S_0,S_1,T,D,R_0,R_1$ before the seals are available.

The refusal clause follows from carrier exhaustion. Since the packet has no coordinate for ambient completeness, quotient equality, host equality, selected limits, or countable choice, the Real-facing handoff can export only the displayed finite stability route.
\end{proof}

\begin{closurestatus}{\CauchyWindowStabilityBridgeUp}
  \constructivestory{A $\CauchyWindowStabilityBridgeUp$ packet is generated from paired StreamName finite windows, a common finite tail-window row, a DyadicRatCore tolerance ledger, paired RegSeqRat readbacks, paired RealUp seals, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-window-stability-bridge-carrier}, \autoref{thm:cauchy-window-stability-bridge-namecert-obligations}, \autoref{thm:cauchy-window-stability-bridge-tail-transport}, and \autoref{thm:cauchy-window-stability-bridge-real-seal-handoff} bind the finite regular-Cauchy tail-window stability bridge.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected limits, quotient stream equality, host equality of real names, countable choice, ambient $\RealUp$ completeness, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, common-tail exactness, dyadic tolerance transport, paired readback stability, Real-seal handoff, and nonescape for the displayed packet.}
\end{closurestatus}
