\chapter{A Concrete Naming Certificate for $\YoungIntegralUp$}
\label{ch:concrete-instances-young-integral-namecert}
\origin{human}

Following Young and Lyons, the $\YoungIntegralUp$ packet records controlled Riemann-sum integration from finite $p$-variation data. It sits beside the bounded-variation carrier of \autoref{ch:concrete-instances-boundedvariation-namecert}, the regulated-function surface of \autoref{ch:concrete-instances-regulated-function-namecert}, the Riemann-sum packet of \autoref{ch:concrete-instances-riemannsum-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names only the finite controlled-sum route; it does not import measure completion, quotient equality of functions, selected refinements, countable choice, or ambient completeness of $\RealUp$.

\begin{definition}[Young integral carrier]
\label{def:young-integral-carrier}
A $\YoungIntegralUp$ carrier is a finite $\BHist$ packet
$$
Y=(F,G,V,C,S,D,R,E,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the regulated integrand row, read through $\RegulatedFunctionUp$ and its finite left/right window data.
\item $G$ is the regulated integrator row, carrying the same interval ledger and endpoint schedule as $F$.
\item $V$ is the $p$-variation and control ledger, recording bounded-variation comparison rows, variation exponents, control steps, and the finite superadditivity checks used by the route.
\item $C$ is the controlled-window row, matching integrand oscillation windows with integrator variation windows before any sum is formed.
\item $S$ is the $\RiemannSumUp$ row listing the tagged partitions, dyadic mesh requests, controlled step values, and finite sum values.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger for mesh radii, variation bounds, and sum-difference margins.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational Cauchy trace of controlled sums.
\item $E$ is the terminal $\RealUp$ integral seal reached only after $F,G,V,C,S,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the integrand, integrator, variation ledger, controlled windows, Riemann-sum row, dyadic ledger, readback, seal, provenance, and local name.
\item $K$ records displayed $\Cont$ replay from a Young-integral request through controlled windows, finite sums, dyadic tolerances, regular readback, and the Real seal.
\item $P$ is the $\Pkg$ provenance over $\YoungIntegralUp$, $\BoundedVariationUp$, $\RegulatedFunctionUp$, $\RiemannSumUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\YoungIntegralUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It has no coordinate for a measure-completion object, quotient equality of functions, an unrecorded refinement selector, a host rough-path lift, countable choice, or ambient Real completeness.
\end{definition}

\begin{theorem}[Young integral NameCert obligations]
\label{thm:young-integral-namecert-obligations}
For every accepted $\YoungIntegralUp$ carrier $Y=(F,G,V,C,S,D,R,E,H,K,P,N)$, the local $\NameCert_{\YoungIntegralUp}$ surface is exhausted by integrand admission, integrator admission, $p$-variation control, controlled-window matching, Riemann-sum formation, dyadic tolerance exactness, regular rational readback, Real-seal handoff, componentwise transport, displayed replay, provenance, and local naming. No accepted consumer may replace those rows by measure completion, quotient function equality, a selected refinement sequence, a host rough-path lift, countable choice, or ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:young-integral-carrier}. The rows $F$ and $G$ expose the regulated integrand and integrator data, while $V$ records the finite variation and control ledger used by the integration route.

The controlled windows are then finite. The row $C$ matches integrand oscillation windows to integrator variation windows, and $S$ forms only the tagged sums displayed by the $\RiemannSumUp$ packet.

The convergence handoff is read through $D,R,E$. Dyadic tolerances in $D$ bound the mesh and sum-difference rows, $R$ records the regular rational trace, and $E$ seals the resulting Real value only after the previous rows have been consumed.

Finally $H,K,P,N$ transport, replay, source, and name that same route. Since the excluded objects have no carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Young integral Riemann-sum handoff]
\label{thm:young-integral-riemann-sum-handoff}
Every accepted $\YoungIntegralUp$ integral read factors through
$$
\RegulatedFunctionUp \longmapsto \BoundedVariationUp \longmapsto \RiemannSumUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
as recorded by $F,G,V,C,S,D,R,E$. The handoff exports a finite controlled Riemann-sum route and no measure-completion integral, quotient function equality, unrecorded refinement selector, host rough-path lift, countable-choice principle, or ambient Real-completeness theorem.
\end{theorem}
\begin{proof}
Start with the integrand and integrator rows. The regulated-function siblings expose the finite endpoint and window data for $F$ and $G$, and the bounded-variation sibling supplies the visible variation ledger read by $V$.

Next form the controlled Riemann sums. The window row $C$ records which integrand and integrator windows are paired, and the $\RiemannSumUp$ row $S$ records the tagged finite sums over those windows.

The tolerance and readback rows then force the terminal route. The dyadic ledger $D$ supplies mesh and sum-difference margins, $R$ records the regular rational trace, and $E$ is the only Real seal available to the consumer.

Transport and replay through $H,K,P,N$ preserve this finite route. Therefore the public integral read cannot escape to measure completion, quotient function equality, a hidden refinement selector, rough-path enhancement, countable choice, or ambient completeness.
\end{proof}

\falsifiablePrediction{An accepted $\YoungIntegralUp$ packet is refuted if a consumer reaches the Real integral seal while omitting the controlled-window row $C$, the Riemann-sum row $S$, the dyadic tolerance row $D$, or the regular readback row $R$.}

\independenceWitness{BoundedVariation, RegulatedFunction, RiemannSum, DyadicRatCore, RegSeqRat, Real: none is bijective with $\YoungIntegralUp$ because the packet jointly carries integrand and integrator rows, a variation-control ledger, controlled windows, finite sums, dyadic tolerances, regular readback, a Real seal, transport, replay, provenance, and local naming.}

\closureat{YoungIntegralUp}{seedStr}

\begin{closurestatus}{\YoungIntegralUp}
  \constructivestory{A $\YoungIntegralUp$ packet is generated from regulated integrand and integrator rows, a p-variation control ledger, controlled Riemann-sum windows, DyadicRatCore tolerances, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:young-integral-carrier}, \autoref{thm:young-integral-namecert-obligations}, and \autoref{thm:young-integral-riemann-sum-handoff} seed the finite controlled-sum route for Young integration.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close measure completion, quotient function equality, selected refinement sequences, host rough-path lifts, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked integrand admission, integrator admission, variation-control exactness, controlled-window matching, Riemann-sum handoff, dyadic tolerance readback, Real-seal nonescape, and structural transport for BEDC.Derived.YoungIntegralUp.}
\end{closurestatus}
