\chapter{A Concrete Naming Certificate for $\MonotoneConvergenceSequenceUp$}
\label{ch:concrete-instances-monotone-convergence-sequence-namecert}
\origin{human}

Following Bishop and Bridges, the $\MonotoneConvergenceSequenceUp$ packet presents bounded monotone sequence convergence as explicit dyadic-window and regular-Cauchy evidence, not as general $\RealUp$ completeness or choice. It sits beside the finite stream-name surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the bounded monotone seal boundary of \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert}. The packet gives downstream Bolzano--Weierstrass, Cauchy completion, and sequence-limit consumers a finite L10 route for monotone convergence without importing ambient completeness.

\begin{definition}[MonotoneConvergenceSequence carrier]
\label{def:monotone-convergence-sequence-carrier}
A $\MonotoneConvergenceSequenceUp$ carrier is a finite $\BHist$ packet
$$
M=(S,L,U,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the monotone sequence source row, carrying the displayed sequence observations and the finite monotonicity classifier read by the packet.
\item $L$ and $U$ are the lower and upper dyadic bound rows, giving the bounded interval in which every inspected source window is certified to land.
\item $W$ is the finite $\StreamNameUp$ window row, exposing only the initial and tail windows requested by the monotone-convergence consumer.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic mesh widths, lower-upper bracket gaps, and tail budgets.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the monotone windows and their dyadic tolerance ledger.
\item $E$ is the $\RealUp$ seal row exposed only after the source, bounds, finite windows, dyadic tolerances, and regular rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for $S,L,U,W,D,R,E$ and the structural rows.
\item $C$ records displayed $\Cont$ replay from monotone source inspection through dyadic bounds, finite windows, tolerance shrinkage, regular readback, and the Real seal.
\item $P$ is the $\Pkg$ provenance over $\MonotoneConvergenceSequenceUp$, $\BoundedMonotoneConvergenceSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MonotoneConvergenceSequenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,L,U,W,D,R,E,H,C,P,N$. It has no coordinate for an unrestricted supremum principle, quotient stream equality, host sequence equality, host real equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[MonotoneConvergenceSequence NameCert obligations]
\label{thm:monotone-convergence-sequence-namecert-obligations}
For every accepted $\MonotoneConvergenceSequenceUp$ carrier
$$
M=(S,L,U,W,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\MonotoneConvergenceSequenceUp}$ surface consists exactly of monotone source exposure through $S$, lower and upper dyadic bound exposure through $L,U$, finite window exposure through $W$, dyadic tolerance accounting through $D$, $\RegSeqRatUp$ readback through $R$, $\RealUp$ seal handoff through $E$, componentwise transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:monotone-convergence-sequence-carrier}. The tuple displays the monotone source row, dyadic bound rows, finite stream windows, dyadic tolerance ledger, regular rational readback, Real seal, and the structural transport, replay, provenance, and naming rows.

The bounded monotone evidence is confined to $S,L,U,W,D$. The source row gives the monotonicity classifier, the bound rows give the visible interval enclosure, and the window and tolerance rows record the finite bracket shrinkage that a consumer may inspect.

The analytic handoff is then $R,E$. The regular rational readback row is obtained only from the displayed windows and dyadic ledger, and the Real seal row is exposed only after that readback has been displayed.

Finally $H,C,P,N$ preserve and name the same finite route. Since the carrier contains no supremum, quotient stream, host sequence equality, host real equality, choice, or ambient completeness coordinate, those objects are outside the local NameCert surface.
\end{proof}

\begin{theorem}[MonotoneConvergenceSequence regular Cauchy route]
\label{thm:monotone-convergence-sequence-regular-cauchy-route}
Every $\RealUp$ or completion-facing consumer of an accepted $\MonotoneConvergenceSequenceUp$ carrier reads the finite route
$$
\BoundedMonotoneConvergenceSealUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The bounded monotone seal supplies the source and interval rows, the finite stream windows expose the inspected observations, the dyadic ledger supplies the tail tolerance budget, and the regular rational readback precedes the terminal Real seal.
\end{theorem}
\begin{proof}
Start with an accepted carrier $M=(S,L,U,W,D,R,E,H,C,P,N)$. The monotone source and bound rows $S,L,U$ are the only coordinates through which bounded monotone evidence can enter the packet.

Read the bounded seal boundary through \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert}. It supplies the public source-and-bound discipline consumed by this carrier, but it does not provide an unrestricted completeness principle.

Next read the finite observation route. The windows $W$ are $\StreamNameUp$ data, the tolerance ledger $D$ is $\DyadicRatCoreUp$ data, and the regular rational row $R$ repacks exactly those displayed windows and tolerances as $\RegSeqRatUp$ readback.

The Real seal $E$ is therefore downstream of the source, dyadic bounds, finite windows, dyadic tolerance ledger, and regular rational readback. Transport and replay through $H,C,P,N$ preserve that same route, so no consumer receives a hidden supremum, quotient stream equality, host sequence equality, host real equality, countable-choice schedule, or ambient Real-completeness witness.
\end{proof}

\closureat{MonotoneConvergenceSequenceUp}{seedStr}

\begin{closurestatus}{\MonotoneConvergenceSequenceUp}
  \constructivestory{A $\MonotoneConvergenceSequenceUp$ packet is generated from a monotone source row, lower and upper dyadic bound rows, finite StreamName windows, a DyadicRatCore tolerance ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:monotone-convergence-sequence-carrier}, \autoref{thm:monotone-convergence-sequence-namecert-obligations}, and \autoref{thm:monotone-convergence-sequence-regular-cauchy-route} seed the bounded monotone regular-Cauchy route over StreamName, DyadicRatCore, RegSeqRat, RealUp, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a general supremum principle, quotient stream equality, host sequence equality, host real equality, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, bounded monotone seal handoff, dyadic bracket shrinkage, RegSeqRat readback exactness, RealUp seal nonescape, and completeness-refusal proofs for BEDC.Derived.MonotoneConvergenceSequenceUp.}
\end{closurestatus}
