\providecommand{\CompactContinuousImageTotalBoundedUp}{\mathsf{CompactContinuousImageTotalBounded}^{\uparrow}}

\chapter{A Concrete Naming Certificate for $\CompactContinuousImageTotalBoundedUp$}
\label{ch:concrete-instances-compact-continuous-image-total-bounded-namecert}
\origin{human}

Following Bishop and Bridges constructive compact metric analysis, the $\CompactContinuousImageTotalBoundedUp$ packet records the finite theorem-facing route by which a continuous image of compact metric data becomes totally bounded. It consumes the compact finite-net surface of \autoref{ch:concrete-instances-compact-namecert}, the continuous-map graph and modulus rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the source and target metric-distance rows, the uniform-modulus ledger, and the rational lower-bound fold. The packet is a concrete image-total-bounded carrier, not a semantic compact-image theorem in an ambient topology.

\begin{definition}[Compact continuous image total-bounded carrier]
\label{def:compact-continuous-image-total-bounded-carrier}
A $\CompactContinuousImageTotalBoundedUp$ carrier is a finite $\BHist$ packet
$$
K=(X,F,U,M,R,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the compact metric finite-net packet, exposing source centers and coverage rows through $\CompactMetricUp$ and the compact carrier.
\item $F$ is the $\ContinuousMapUp$ pointwise-modulus and graph packet from the source metric carrier to the target metric carrier.
\item $U$ is the $\UniformModulusUp$ ledger read from the compact finite-net and continuous-map route.
\item $M$ is the source and target $\MetricUp$ distance row pair, carrying only displayed distance witnesses.
\item $R$ is the $\RatUp$ lower-bound fold row used to select finite image radii from the displayed modulus and net data.
\item $B$ is the $\ProbeBundle$ image-center row obtained by applying the displayed graph rows of $F$ to the finite source-center bundle of $X$.
\item $H$ records componentwise $\hsame$ transport for $X,F,U,M,R,B$ and the local structural rows.
\item $C$ records displayed $\Cont$ replay from compact source nets through continuous-map modulus rows, target distance rows, rational folds, and image-center bundle rows.
\item $P$ is the $\Pkg$ provenance over $\CompactContinuousImageTotalBoundedUp$, $\CompactMetricUp$, $\CompactUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\MetricUp$, $\RatUp$, $\ProbeBundle$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactContinuousImageTotalBoundedUp}$ row.
\end{enumerate}
The carrier contains no open-cover compactness object, no selected subcover from an arbitrary cover, no host image set, no quotient function equality, no choice-selected center, and no ambient completeness principle.
\end{definition}

\begin{theorem}[CompactContinuousImageTotalBounded NameCert obligations]
\label{thm:compact-continuous-image-total-bounded-namecert-obligations}
For every accepted $\CompactContinuousImageTotalBoundedUp$ carrier $K=(X,F,U,M,R,B,H,C,P,N)$, the local $\NameCert_{\CompactContinuousImageTotalBoundedUp}$ surface consists exactly of these finite obligation rows:
\begin{enumerate}
\item carrier admission for compact metric finite-net data, continuous-map rows, uniform-modulus ledger, metric-distance rows, rational lower-bound fold, image-center bundle, transport, replay, provenance, and local naming;
\item finite-net image classification, requiring every image center to arise from a bundled compact source center and a displayed $\ContinuousMapUp$ graph row;
\item modulus compatibility, requiring the $\UniformModulusUp$ ledger to use the same compact source, continuous-map, metric-distance, and $\RatUp$ fold rows;
\item total-bounded export, requiring every target-image coverage read to factor through the finite $\ProbeBundle$ image-center row $B$;
\item refusal of open-cover compactness, arbitrary selected subcovers, host image sets, quotient function equality, choice-selected centers, and ambient completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-continuous-image-total-bounded-carrier}. The tuple displays the compact source net, continuous graph and modulus data, uniform-modulus ledger, metric rows, rational fold, image centers, transport, replay, provenance, and local naming.

Finite-net image classification is the route $X,F,B$. Each image center is read by applying the displayed continuous-map graph row to a center already present in the compact source bundle, so no host image set or arbitrary center selector is introduced.

Modulus compatibility is the route $X,F,U,M,R$. The uniform-modulus ledger is obtained from the compact finite-net data, the continuous-map pointwise rows, the source and target metric distances, and the rational lower-bound fold over $\RatUp$ histories.

The total-bounded export is $B$ with its support rows. A target-image coverage read must pass through the finite $\ProbeBundle$ image-center row and the displayed target metric row before it reaches any consumer.

Finally, $H,C,P,N$ preserve and name exactly this route. Since the carrier has no open-cover compactness object, arbitrary subcover selector, host image-set coordinate, quotient function equality, choice-selected center, or completeness coordinate, those objects cannot be exported.
\end{proof}

\begin{theorem}[Compact continuous image total-bounded handoff]
\label{thm:compact-continuous-image-total-bounded-handoff}
Every total-boundedness consumer of an accepted $\CompactContinuousImageTotalBoundedUp$ carrier receives only the compact finite-net source row, the continuous-map graph and modulus rows, the uniform-modulus ledger, source and target metric-distance rows, the $\RatUp$ lower-bound fold, the finite $\ProbeBundle$ image centers, and the visible structural rows
$$
X,F,U,M,R,B,H,C,P,N .
$$
The handoff is therefore a finite BEDC certificate for image total-boundedness, not an open-cover compactness theorem and not a host image construction.
\end{theorem}
\begin{proof}
Begin with the accepted carrier and project its rows. The only source compactness data available are the finite-net rows in $X$.

Read the continuous map through $F$ and the uniform modulus through $U$. Both rows are tied to the same source and target metric-distance rows $M$, so the image read cannot change its metric carrier mid-route.

The rational lower-bound fold $R$ and the image-center bundle $B$ produce the target finite-net witness. The fold is a finite $\RatUp$ history calculation, and the image centers are a finite $\ProbeBundle$ list, so no arbitrary subcover or choice-selected image point is exposed.

The structural rows $H,C,P,N$ transport, replay, prove provenance, and name that finite route. The excluded open-cover, host-image, quotient-function, choice, and completeness objects are absent from the packet.
\end{proof}

\begin{closurestatus}{\CompactContinuousImageTotalBoundedUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-continuous-image-total-bounded-carrier}, \autoref{thm:compact-continuous-image-total-bounded-namecert-obligations}, and \autoref{thm:compact-continuous-image-total-bounded-handoff} seed the compact-continuous-image total-bounded carrier over compact finite nets, continuous-map modulus rows, uniform-modulus ledgers, metric distances, RatUp folds, ProbeBundle image centers, hsame transport, Cont replay, Pkg provenance, and local NameCert data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, arbitrary subcovers, host image sets, quotient function equality, choice-selected centers, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net image classification, modulus compatibility, total-bounded export, and non-escape for BEDC.Derived.CompactContinuousImageTotalBoundedUp.}
  \constructivestory{A $\CompactContinuousImageTotalBoundedUp$ packet is generated from CompactMetric finite-net data, ContinuousMap pointwise-modulus rows, UniformModulus ledgers, source and target MetricSpace distance rows, RatUp lower-bound folds, ProbeBundle image centers, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
