\chapter{A Concrete Naming Certificate for $\HyperbolicPoissonKernelUp$}
\label{ch:concrete-instances-hyperbolic-poisson-kernel-namecert}
\origin{ai}

The $\HyperbolicPoissonKernelUp$ packet realizes the boundary-weighted disk-read branch of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits beside the hyperbolic metric surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the boundary-shadow route of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, the visual metric packet of \autoref{ch:concrete-instances-hyperbolic-visual-metric-namecert}, the unit-disk carrier of \autoref{ch:concrete-instances-unitdisk-namecert}, the circle carrier of \autoref{ch:concrete-instances-s1-namecert}, the integral row of \autoref{ch:concrete-instances-integral-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite boundary-kernel read, not a completed harmonic boundary theory.

\begin{definition}[Hyperbolic Poisson-kernel carrier]
\label{def:hyperbolic-poisson-kernel-carrier}
A $\HyperbolicPoissonKernelUp$ carrier is a finite $\BHist$ packet
$$
K=(D,M,B,V,U,S,I,R,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ disk-source row for the interior point being read.
\item $M$ is the $\HyperbolicMetricUp$ metric row attached to the same disk source.
\item $B$ is the $\HyperbolicBoundaryShadowUp$ boundary-shadow row that exposes the visible boundary window.
\item $V$ is the $\HyperbolicVisualMetricUp$ visual-boundary comparison row.
\item $U$ is the $\SOneUp$ boundary-circle row over which angular samples are displayed.
\item $S$ is the $\IntegralUp$ boundary-integration row for the finite sample or displayed quadrature route.
\item $I$ is the $\RealUp$ scalar endpoint row for kernel weights and normalization comparisons.
\item $R$ is the radial denominator and numerator ledger tying $D,M,B,U,I$ to the displayed hyperbolic Poisson weight.
\item $W$ is the weighted boundary-integral readback row, exposing only the value determined by $S,R,I$ over the displayed disk and boundary rows.
\item $H$ records componentwise $\hsame$ transport for $D,M,B,V,U,S,I,R,W,C,P,N$.
\item $C$ records displayed $\Cont$ replay from disk source through metric, boundary shadow, visual boundary, circle, integral, weight, and readback rows.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicPoissonKernelUp$, $\HyperbolicMetricUp$, $\HyperbolicBoundaryShadowUp$, $\HyperbolicVisualMetricUp$, $\UnitDiskUp$, $\SOneUp$, $\IntegralUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicPoissonKernelUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for completed boundary functions, unrestricted harmonic extension, selected radial limits, quotient boundary equality, ultrafilter convergence, or global boundary compactification.
\end{definition}

\begin{theorem}[Hyperbolic Poisson-kernel NameCert obligations]
\label{thm:hyperbolic-poisson-kernel-namecert-obligations}
For every accepted $\HyperbolicPoissonKernelUp$ carrier $K=(D,M,B,V,U,S,I,R,W,H,C,P,N)$, the local $\NameCert_{\HyperbolicPoissonKernelUp}$ surface consists exactly of disk-source admission, hyperbolic metric admission, boundary-shadow admission, visual-boundary comparison, circle-boundary admission, boundary-integral admission, Real endpoint admission, radial weight-ledger exactness, weighted readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-poisson-kernel-carrier}. The disk, metric, boundary-shadow, visual-boundary, circle, integral, Real, weight, readback, transport, replay, provenance, and local naming rows are the full public inventory.

The geometric rows are read first. The disk row $D$ fixes the interior source, $M$ fixes the hyperbolic metric comparison, $B$ fixes the visible boundary shadow, and $V$ fixes the visual-boundary comparison.

The boundary-kernel rows are then read through $U,S,I,R,W$. The circle row supplies boundary samples, the integral row supplies the displayed boundary aggregation, the Real row supplies scalar endpoints, the weight ledger supplies the hyperbolic Poisson factor, and the readback row exposes only the value determined by those rows.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since no further row is present, completed boundary functions, unrestricted harmonic extension, selected limits, quotient boundary equality, ultrafilter convergence, and global compactification are outside the packet.
\end{proof}

\begin{theorem}[Hyperbolic Poisson-kernel boundary integral nonescape]
\label{thm:hyperbolic-poisson-kernel-boundary-integral-nonescape}
Every accepted boundary-integral read of a $\HyperbolicPoissonKernelUp$ carrier factors through the finite route
$$
\UnitDiskUp,\ \HyperbolicMetricUp,\ \HyperbolicBoundaryShadowUp,\ \HyperbolicVisualMetricUp,\ \SOneUp,\ \IntegralUp,\ \RealUp .
$$
The route first fixes the disk, metric, boundary-shadow, and visual-boundary rows, then reads the circle and integral rows, then reads the Real endpoint and weight ledger rows, and only then exposes weighted boundary readback. It exports no completed boundary function, unrestricted harmonic extension, selected radial limit, quotient boundary equality, ultrafilter convergence, or global compactification.
\end{theorem}
\begin{proof}
Let $K=(D,M,B,V,U,S,I,R,W,H,C,P,N)$ be accepted. A boundary-integral consumer first receives the geometric route $D,M,B,V$, so the boundary window is the one displayed by the disk, metric, shadow, and visual rows.

The integration route is $U,S$. The circle row supplies the boundary parameter window, and the integral row supplies only the displayed finite or certified aggregation over that window.

The scalar kernel route is $I,R,W$. The Real row supplies the endpoints, the weight ledger ties those endpoints to the disk and boundary rows, and the readback row exposes the weighted value only after the integral and weight ledgers are fixed.

Transport, replay, provenance, and local naming through $H,C,P,N$ preserve this route. The excluded analytic and choice-theoretic objects have no carrier coordinate, so the boundary-integral read cannot escape the finite packet.
\end{proof}

\falsifiablePrediction{Removing either the $\HyperbolicMetricUp$ row $M$ or the $\HyperbolicBoundaryShadowUp$ row $B$ makes \autoref{thm:hyperbolic-poisson-kernel-boundary-integral-nonescape} false: a consumer could no longer verify that the boundary weight belongs to the displayed hyperbolic disk route.}

\independenceWitness{hyperbolicmetric, hyperbolic-boundary-shadow, unitdisk, sone, integral, real: $\HyperbolicPoissonKernelUp$ is not bijective to any listed sibling because it jointly carries disk source, hyperbolic metric, boundary shadow, visual comparison, circle boundary, integral aggregation, Real endpoints, weight ledger, readback, transport, replay, provenance, and local naming rows.}

The Lean TasteGate site for $\HyperbolicPoissonKernelUp$ must provide explicit $\mathsf{Nontrivial}\ \HyperbolicPoissonKernelUp$ and $\mathsf{FieldFaithful}\ \HyperbolicPoissonKernelUp$ instances. These instances keep the disk, metric, boundary, circle, integral, Real, weight, readback, transport, replay, provenance, and naming rows distinguishable.

\closureat{HyperbolicPoissonKernelUp}{seedStr}

\begin{closurestatus}{\HyperbolicPoissonKernelUp}
  \constructivestory{A $\HyperbolicPoissonKernelUp$ packet is generated from UnitDiskUp disk data, HyperbolicMetricUp metric rows, HyperbolicBoundaryShadowUp and HyperbolicVisualMetricUp boundary rows, SOneUp circle rows, IntegralUp boundary aggregation, RealUp endpoints, a hyperbolic weight ledger, weighted readback, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-poisson-kernel-carrier}, \autoref{thm:hyperbolic-poisson-kernel-namecert-obligations}, and \autoref{thm:hyperbolic-poisson-kernel-boundary-integral-nonescape} seed the finite hyperbolic boundary-kernel route over disk, metric, boundary, circle, integral, Real, transport, replay, provenance, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim completed boundary functions, unrestricted harmonic extension, selected radial limits, quotient boundary equality, ultrafilter convergence, global boundary compactification, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, geometric boundary routing, circle and integral admission, weight-ledger exactness, readback nonescape, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming for BEDC.Derived.HyperbolicPoissonKernelUp.}
\end{closurestatus}
