\chapter{A Concrete Naming Certificate for $\CauchyCompletionReflectorComparisonUp$}
\label{ch:concrete-instances-cauchy-completion-reflector-comparison-namecert}
\origin{human}

Following Bishop and Bridges constructive completion and Bourbaki's universal-mapping language, the $\CauchyCompletionReflectorComparisonUp$ packet records one finite BEDC certificate comparing the reflector, comparison, adjunction, and monad presentations of Cauchy completion. It reads the reflector route of \autoref{ch:concrete-instances-cauchycompletionreflector-namecert}, the comparison surface of \autoref{ch:concrete-instances-cauchy-completion-comparison-namecert}, the adjunction handoff of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert}, and the monad schedule of \autoref{ch:concrete-instances-cauchycompletionmonad-namecert} through the same finite real-seal route. The packet names the common certificate surface only; it does not construct quotient completions, choose representatives, identify host objects, or appeal to ambient completeness of $\RealUp$.

\begin{definition}[CauchyCompletionReflectorComparison carrier]
\label{def:cauchy-completion-reflector-comparison-carrier}
A $\CauchyCompletionReflectorComparisonUp$ carrier is a finite $\BHist$ packet
$$
K=(\rho,K_0,A,M,W,Q,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $\rho$ is the $\CauchyCompletionReflectorUp$ row exposing unit, counit, idempotent, extension, reflection, and local real-transport data.
\item $K_0$ is the $\CauchyCompletionComparisonUp$ row exposing the comparison between unit-and-universal-property and functorial metric-completion presentations.
\item $A$ is the $\CauchyCompletionAdjunctionUp$ row exposing the finite unit-counit handoff surface.
\item $M$ is the $\CauchyCompletionMonadUp$ row exposing the finite schedule, diagonal readback, and monad composition boundary.
\item $W$ is the shared $\StreamNameUp$ window route inspected by all four completion presentations.
\item $Q$ is the shared $\RegSeqRatUp$ readback route reached after the displayed windows.
\item $D$ is the shared $\DyadicRatCoreUp$ tolerance ledger attached to the same window route.
\item $E$ is the terminal $\RealUp$ seal reached only after $W,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the four presentation rows, the shared real-seal rows, replay, provenance, and naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
\rho,K_0,A,M \longmapsto W,D,Q \longmapsto E \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionReflectorComparisonUp$, $\CauchyCompletionReflectorUp$, $\CauchyCompletionComparisonUp$, $\CauchyCompletionAdjunctionUp$, $\CauchyCompletionMonadUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionReflectorComparisonUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these twelve rows and their displayed transports. It has no coordinate for quotient completion equality, selected representatives, countable choice, host equality of completed objects, open-cover compactness, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[CauchyCompletionReflectorComparison NameCert obligations]
\label{thm:cauchy-completion-reflector-comparison-namecert-obligations}
For every accepted $\CauchyCompletionReflectorComparisonUp$ carrier
$$
K=(\rho,K_0,A,M,W,Q,D,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionReflectorComparisonUp}$ surface consists exactly of reflector-route admission through $\rho$; comparison-route exposure through $K_0$; adjunction handoff through $A$; monad schedule compatibility through $M$; shared finite real-seal routing through $W,D,Q,E$; componentwise transport through $H$; replay through $C$; provenance through $P$; and local naming through $N$. It exports no quotient completion, selected representative, countable choice, host equality, open-cover compactness, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is tuple projection from \autoref{def:cauchy-completion-reflector-comparison-carrier}. The accepted packet displays exactly the four presentation rows, the shared window-tolerance-readback-seal route, and the structural rows.

The reflector, comparison, adjunction, and monad rows are then read as sibling routes. The row $\rho$ contributes the reflector route, $K_0$ contributes the comparison route, $A$ contributes the adjunction handoff, and $M$ contributes the schedule and diagonal-readback compatibility. None of these rows contains an independent terminal seal.

The common real-facing route is exhausted by $W,D,Q,E$. A consumer must inspect the finite $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ tolerance ledger, and the $\RegSeqRatUp$ readback before reaching the terminal $\RealUp$ seal.

Finally $H,C,P,N$ transport, replay, source, and name only the displayed packet. Since no further coordinate remains in the carrier, quotient completions, selected representatives, countable choice, host equality, open-cover compactness, and ambient $\RealUp$ completeness cannot be exported.
\end{proof}

\closureat{CauchyCompletionReflectorComparisonUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionReflectorComparisonUp}
  \constructivestory{A $\CauchyCompletionReflectorComparisonUp$ packet is generated from reflector, comparison, adjunction, and monad presentation rows, shared StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-reflector-comparison-carrier} and \autoref{thm:cauchy-completion-reflector-comparison-namecert-obligations} seed the finite certificate comparing reflector, comparison, adjunction, and monad completion presentations over one shared real-seal route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host equality, open-cover compactness, $\RealUp$ completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, reflector-route admission, comparison-route exposure, adjunction handoff, monad schedule compatibility, shared real-seal routing, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCompletionReflectorComparisonUp.}
\end{closurestatus}
