\chapter{A Concrete Naming Certificate for $\LocatedCauchySubsequenceUp$}
\label{ch:concrete-instances-located-cauchy-subsequence-namecert}
\origin{human}

Following Bishop and Bridges, the $\LocatedCauchySubsequenceUp$ packet records the finite route by which located regular rational windows expose a Cauchy subsequence handoff to the Real and Completion corridor. It consumes the located tail-window discipline of \autoref{ch:concrete-instances-located-regseqrat-namecert}, the finite extraction surface of \autoref{ch:concrete-instances-cauchy-subsequence-extraction-namecert}, the cofinal regular-subsequence stability row of \autoref{ch:concrete-instances-regular-cauchy-subsequence-stability-namecert}, the stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a displayed subsequence extraction surface for located regular names; it is not a selected infinite subsequence, quotient stream equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[LocatedCauchySubsequence carrier]
\label{def:located-cauchy-subsequence-carrier}
A $\LocatedCauchySubsequenceUp$ carrier is a finite $\BHist$ packet
$$
L=(W,R,D,Q,I,S,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\StreamNameUp$ window ledger, listing the source windows and selected subsequence windows inspected by the packet.
\item $R$ is the $\RegSeqRatUp$ readback row for the located regular rational source.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by Cauchy and locatedness requests.
\item $Q$ is the $\LocatedRegSeqRatUp$ comparison row, exposing located tail windows and finite cut comparisons.
\item $I$ is the subsequence-index row, recording the monotone selected indices and the source windows from which they are read.
\item $S$ is the $\CauchySubsequenceExtractionUp$ stability row, binding the extracted windows to the Cauchy tolerance schedule.
\item $E$ is the $\RealUp$ seal row, available only after $W,R,D,Q,I,S$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the window, readback, tolerance, located-comparison, index, extraction, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the same finite route.
\item $P$ is the $\Pkg$ provenance over $\LocatedCauchySubsequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\LocatedRegSeqRatUp$, $\CauchySubsequenceExtractionUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCauchySubsequenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,R,D,Q,I,S,E,H,C,P,N$. It has no coordinate for a choice-selected infinite subsequence, quotient stream equality, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[LocatedCauchySubsequence NameCert obligations]
\label{thm:located-cauchy-subsequence-namecert-obligations}
For every accepted $\LocatedCauchySubsequenceUp$ carrier
$$
L=(W,R,D,Q,I,S,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedCauchySubsequenceUp}$ surface consists exactly of five obligation families: carrier admission for $W,R,D,Q,I,S,E,H,C,P,N$; located-window exposure through the $\LocatedRegSeqRatUp$ row $Q$; subsequence extraction stability through the index row $I$ and extraction row $S$; $\RealUp$ handoff through the seal row $E$; and refusal of selected subsequences, quotient stream equality, countable choice, trichotomy, host real equality, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:located-cauchy-subsequence-carrier}. The packet displays exactly the stream windows, regular rational readback, dyadic tolerance ledger, located comparison row, subsequence-index row, extraction row, seal row, transport, replay, provenance, and local naming.

Located-window exposure is inherited from \autoref{ch:concrete-instances-located-regseqrat-namecert}. A location request must pass through $Q$ after reading the finite windows $W$, the regular rational row $R$, and the dyadic tolerance ledger $D$.

Subsequence extraction stability is the pair of rows $I,S$. The index row states which source windows are selected, and the extraction row states that the selected windows meet the displayed Cauchy tolerance schedule. Componentwise transport $H$ and replay $C$ preserve that route without adding a new selector.

The real-facing handoff is terminal at $E$. Since $E$ is only reachable after $W,R,D,Q,I,S,H,C,P,N$ have been displayed, it exports a finite located subsequence seal and not a quotient completion or ambient completeness principle.

The classifier has no remaining coordinate beyond the listed rows. Thus selected subsequences, quotient stream equality, countable choice, trichotomy, host real equality, and ambient $\RealUp$ completeness are refused by the carrier surface itself.
\end{proof}

\begin{theorem}[LocatedCauchySubsequence located-window exposure]
\label{thm:located-cauchy-subsequence-located-window-exposure}
Every accepted $\LocatedCauchySubsequenceUp$ carrier exposes a located subsequence window only through the finite route
$$
W,R,D,Q,I,S,H,C,P,N.
$$
In particular, the subsequence-index row cannot be consumed before the source $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, and $\LocatedRegSeqRatUp$ comparison row have been displayed.
\end{theorem}
\begin{proof}
Project the rows of \autoref{def:located-cauchy-subsequence-carrier}. A located subsequence request first names a source observation window in $W$, reads the rational source through $R$, and consults the dyadic tolerance ledger $D$.

The located comparison row $Q$ then decides the displayed tail-window comparison. Only after that row is present may the index row $I$ and extraction row $S$ expose the selected subsequence window.

Transport, replay, provenance, and local naming preserve the same route. No row in the packet allows $I$ to be read independently of $W,R,D,Q$.
\end{proof}

\begin{theorem}[LocatedCauchySubsequence RealUp handoff]
\label{thm:located-cauchy-subsequence-realup-handoff}
Every $\RealUp$-facing consumer of an accepted $\LocatedCauchySubsequenceUp$ carrier factors through the located regular source, subsequence-index row, and extraction-stability row before reading the seal row. The handoff exposes only finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerances, $\LocatedRegSeqRatUp$ comparison rows, subsequence-index rows, $\CauchySubsequenceExtractionUp$ stability rows, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Begin with a Real-facing read. The seal row $E$ is downstream of the source windows $W$, readback $R$, dyadic ledger $D$, located comparison row $Q$, index row $I$, and extraction row $S$.

Apply \autoref{thm:located-cauchy-subsequence-namecert-obligations}. The obligation surface forces every consumer-visible read to pass through those finite rows before the seal can be exposed.

The remaining structural rows only transport and replay the same displayed data. Therefore the handoff is a finite BEDC route from located regular rational windows to a terminal $\RealUp$ seal, not an ambient completion theorem.
\end{proof}

\falsifiablePrediction{Every $\LocatedCauchySubsequenceUp$ read factors through displayed $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerances, $\LocatedRegSeqRatUp$ comparison rows, subsequence-index rows, $\CauchySubsequenceExtractionUp$ stability rows, a $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{locatedregseqrat, cauchysubsequenceextraction, regularcauchysubsequencestability, streamname, regseqrat, dyadicratcore, real: $\LocatedCauchySubsequenceUp$ is not bijective to any listed sibling because it jointly carries located tail-window comparisons, monotone selected indices, extraction stability, finite stream windows, regular rational readback, dyadic tolerances, Real seal routing, transport, replay, provenance, and local naming in one packet.}

\closureat{LocatedCauchySubsequenceUp}{seedStr}

\begin{closurestatus}{\LocatedCauchySubsequenceUp}
  \constructivestory{A $\LocatedCauchySubsequenceUp$ packet is generated from StreamName source and subsequence windows, RegSeqRat readback, DyadicRatCore tolerance rows, LocatedRegSeqRat comparison rows, subsequence-index rows, CauchySubsequenceExtraction stability rows, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-cauchy-subsequence-carrier}, \autoref{thm:located-cauchy-subsequence-namecert-obligations}, \autoref{thm:located-cauchy-subsequence-located-window-exposure}, and \autoref{thm:located-cauchy-subsequence-realup-handoff} seed the finite located Cauchy subsequence route from displayed regular rational windows to Real-facing handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, selected infinite subsequences, quotient stream equality, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, located-window exposure, subsequence extraction stability, RealUp handoff, and nonescape for BEDC.Derived.LocatedCauchySubsequenceUp.}
\end{closurestatus}
