\chapter{A Concrete Naming Certificate for $\RegularCauchyPicardSealUp$}
\label{ch:concrete-instances-regular-cauchy-picard-seal-namecert}
\origin{human}

Following Banach's contraction principle and Bishop--Bridges constructive analysis, the $\RegularCauchyPicardSealUp$ packet records the finite route by which a displayed Picard orbit is read as a regular rational Cauchy name and then sealed as a $\RealUp$ object. It sits over the orbit rows of \autoref{ch:concrete-instances-picard-iteration-namecert}, the contraction ledger of \autoref{ch:concrete-instances-banach-fixed-point-namecert}, the precision schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, and the bounded ambient interface of \autoref{ch:concrete-instances-completemetric-namecert}. The packet is deliberately finite: it certifies the route from named Picard rows to a regular Cauchy seal, not an unrestricted fixed-point selection theorem.

\begin{definition}[Regular Cauchy Picard seal carrier]
\label{def:regular-cauchy-picard-seal-carrier}
A $\RegularCauchyPicardSealUp$ carrier is a finite $\BHist$ packet
$$
R=(I,B,M,Q,E,H,C,P,N)
$$
whose rows have the following roles.
\begin{enumerate}
\item $I$ is a finite $\PicardIterationUp$ orbit row displaying the initial point, the iterated contraction rows, and the finite prefix consumed by the certificate.
\item $B$ is a $\BanachFixedPointUp$ contraction-budget row exposing only the local Lipschitz decrease data needed to compare successive Picard rows.
\item $M$ is a $\CauchyModulusUp$ schedule extracted from the displayed contraction budget and attached to finite precision requests.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the finite Picard orbit and the modulus schedule.
\item $E$ is the terminal $\RealUp$ seal reached through the displayed regular rational readback.
\item $H,C,P,N$ are respectively the componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\RegularCauchyPicardSealUp}$ row.
\end{enumerate}
The carrier contains no coordinate for a selected fixed point, host function extensionality, quotient stream equality, ambient completeness, or an unrestricted Banach fixed-point existence principle.
\end{definition}

\begin{theorem}[Regular Cauchy Picard seal obligations]
\label{thm:regular-cauchy-picard-seal-namecert-obligations}
For every accepted carrier $R=(I,B,M,Q,E,H,C,P,N)$ of \autoref{def:regular-cauchy-picard-seal-carrier}, the local $\NameCert_{\RegularCauchyPicardSealUp}$ surface consists exactly of the Picard orbit row $I$, the contraction-budget row $B$, the extracted modulus row $M$, the regular rational readback row $Q$, the terminal $\RealUp$ seal row $E$, and the structural rows $H,C,P,N$. A downstream consumer must read the rows in the displayed order
$$
I \to B \to M \to Q \to E \to H,C,P,N .
$$
No accepted obligation row can be replaced by a selected fixed point, a host-level proof that two functions are extensionally equal, quotient equality between stream representatives, an ambient completeness theorem, or an unrestricted Banach fixed-point existence row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-picard-seal-carrier}. The analytic rows are exactly the finite Picard orbit, contraction budget, extracted modulus, regular rational readback, and terminal Real seal; the remaining rows are the standard BEDC transport, replay, provenance, and naming surface.

The Picard row is read first because the modulus schedule is extracted from finite comparisons between displayed iterates. The contraction-budget row supplies those comparisons, and the $\CauchyModulusUp$ row records the precision threshold as data rather than as a host completeness argument.

The $\RegSeqRatUp$ readback can then consume only the displayed orbit prefix and the extracted modulus. Once that readback is present, the $\RealUp$ seal is reached through the same regular Cauchy route used by the surrounding Real-and-Completion chapters.

Finally the rows $H,C,P,N$ transport and replay this finite route as the local certificate. Since none of the carrier coordinates stores a selected fixed point, function extensionality principle, quotient stream equality, ambient completeness theorem, or unrestricted fixed-point existence theorem, no consumer of the NameCert surface can obtain those claims from this packet.
\end{proof}

\begin{theorem}[Regular Cauchy Picard seal route]
\label{thm:regular-cauchy-picard-seal-route}
Let $R=(I,B,M,Q,E,H,C,P,N)$ be an accepted $\RegularCauchyPicardSealUp$ carrier. Every finite precision request for the Real-facing Picard limit factors through the route
$$
\PicardIterationUp \longmapsto \BanachFixedPointUp \longmapsto \CauchyModulusUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The route first reads a finite Picard orbit prefix, then extracts a Cauchy modulus from the contraction budget, then performs $\RegSeqRatUp$ readback, and only then reaches the terminal $\RealUp$ seal. It does not claim a chosen fixed point, host function extensionality, quotient stream equality, ambient completeness, or unrestricted Banach fixed-point existence.
\end{theorem}
\begin{proof}
Begin with the accepted carrier and the obligation theorem above. They force every precision request to start with the displayed finite Picard orbit $I$ and the contraction budget $B$.

Next extract the modulus row $M$. This step is finite: a requested precision is matched with a displayed threshold from the contraction ledger, so the certificate does not invoke a global completeness principle or a choice schedule over all requests.

Use the extracted threshold to read the regular rational row $Q$. The readback is the ordinary $\RegSeqRatUp$ passage from finite rational data and a modulus to a regular Cauchy name; it has no quotient-stream coordinate and no host equality coordinate.

Finally pass from $Q$ to the terminal Real seal $E$ and replay the route through $H,C,P,N$. The resulting seal records the finite Picard-to-regular-Cauchy route, while the selected fixed point and unrestricted Banach existence claims remain outside the carrier.
\end{proof}

\begin{closurestatus}{\RegularCauchyPicardSealUp}
  \constructivestory{A $\RegularCauchyPicardSealUp$ packet is generated from a finite $\PicardIterationUp$ orbit prefix, a $\BanachFixedPointUp$ contraction-budget row, an extracted $\CauchyModulusUp$ precision schedule, a $\RegSeqRatUp$ readback row, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-picard-seal-carrier}, \autoref{thm:regular-cauchy-picard-seal-namecert-obligations}, and \autoref{thm:regular-cauchy-picard-seal-route} seed the finite Picard-orbit route from contraction data through modulus extraction, regular rational readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected fixed points, host function extensionality, quotient stream equality, ambient completeness, or unrestricted Banach fixed-point existence.}
  \upgradepath{A formal route can encode the finite carrier rows and prove the Picard-orbit modulus extraction, regular rational readback, and terminal Real-seal route.}
\end{closurestatus}
