\chapter{A Concrete Naming Certificate for $\WobbleSaturationSealUp$}
\label{ch:concrete-instances-wobble-saturation-seal-namecert}
\origin{ai}

The $\WobbleSaturationSealUp$ packet realizes the $f_{3}$ directional saturation route of \autoref{thm:philosophy-wobble-saturation-presentation} as finite NameCert data. It consumes the six-coordinate codon window of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the DNA boundary-tile classifier of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the six-boundary coverage packet of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, the wobble quotient spectral trigger of \autoref{ch:concrete-instances-wobble-quotient-spectral-trigger-namecert}, and the radial wobble spectrum of \autoref{ch:concrete-instances-radial-wobble-spectrum-namecert}. The packet names the unique non-leaking $f_{3}$ saturation seal; it is not a biological stochastic model, quotient codon semantics, or an unrestricted support-closure oracle.

\begin{definition}[Wobble saturation seal carrier]
\label{def:wobble-saturation-seal-carrier}
A $\WobbleSaturationSealUp$ carrier is a finite $\BHist$ packet
$$
S=(W,T,C,Q,R,D,A,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ row exposing the six Boolean coordinates of the inspected codon window.
\item $T$ is the $\DnaWindowSixBoundaryTileUp$ row naming the boundary tile through which the wobble read is admitted.
\item $C$ is the $\SixBoundaryTileCoverageUp$ row recording finite coverage of the relevant boundary support.
\item $Q$ is the $\WobbleQuotientSpectralTriggerUp$ row exposing the quotient-facing spectral trigger.
\item $R$ is the $\RadialWobbleSpectrumUp$ row exposing the radial spectrum and wobble-edge accounting.
\item $D$ is the directional saturation row, recording that the only non-leaking active-support saturation direction is $f_{3}$.
\item $A$ is the $\mathrm{ACG}$ seal row, recording the median, symmetry, spectral, and final $f_{3}$ sealing corner.
\item $H$ records componentwise $\hsame$ transport for window, boundary-tile, coverage, quotient-trigger, radial-spectrum, saturation, seal, replay, provenance, and naming rows.
\item $K$ records displayed $\Cont$ replay from the six-bit window through boundary coverage, quotient trigger, radial spectrum, and $f_{3}$ seal.
\item $P$ is the $\Pkg$ provenance over $\WobbleSaturationSealUp$, $\CodonSixBitWindowUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\WobbleQuotientSpectralTriggerUp$, $\RadialWobbleSpectrumUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\WobbleSaturationSealUp}$ row.
\end{enumerate}
The classifier accepts a packet only when the $f_{3}$ saturation row is read after the six-bit window, boundary-tile, coverage, quotient-trigger, and radial-spectrum rows, and when the $\mathrm{ACG}$ seal is the displayed terminal corner for that same route.
\end{definition}

\begin{theorem}[Wobble saturation seal NameCert obligations]
\label{thm:wobble-saturation-seal-namecert-obligations}
For every accepted $\WobbleSaturationSealUp$ carrier $S=(W,T,C,Q,R,D,A,H,K,P,N)$, the local $\NameCert_{\WobbleSaturationSealUp}$ surface consists exactly of six-bit window admission through $W$, boundary-tile admission through $T$, six-boundary coverage through $C$, quotient spectral triggering through $Q$, radial wobble-spectrum exposure through $R$, unique $f_{3}$ directional saturation through $D$, $\mathrm{ACG}$ seal exposure through $A$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $K$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:wobble-saturation-seal-carrier}. The rows $W,T,C,Q,R,D,A,H,K,P,N$ are the complete displayed inventory.

Read the support rows first. The six-bit window, boundary-tile, and coverage rows identify the finite codon support surface before any wobble saturation is visible.

Read the wobble rows next. The quotient spectral trigger $Q$ and radial spectrum $R$ supply the two sibling wobble surfaces, and $D$ records the unique non-leaking $f_{3}$ direction over that shared surface. The row $A$ then exposes $\mathrm{ACG}$ as the terminal seal for the same route.

Finally $H,K,P,N$ transport, replay, source, and name exactly those rows. Since the carrier has no stochastic, quotient-semantic, or unrestricted support-closure coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Wobble saturation seal nonescape]
\label{thm:wobble-saturation-seal-nonescape}
Every accepted $\WobbleSaturationSealUp$ consumer must read $\CodonSixBitWindowUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\WobbleQuotientSpectralTriggerUp$, and $\RadialWobbleSpectrumUp$ before the unique $f_{3}$ saturation seal can be exposed. The seal exports no biological stochastic model, quotient codon semantics, unrestricted support closure, or route that treats a leaking direction as equivalent to the displayed $f_{3}$ row.
\end{theorem}
\begin{proof}
Apply the obligation theorem. It places the six-bit window, boundary tile, coverage, quotient trigger, and radial spectrum before the directional saturation row.

The nonescape claim is then a carrier-inventory statement. The rows $D$ and $A$ name the unique $f_{3}$ saturation route and the terminal $\mathrm{ACG}$ seal, while $H,K,P,N$ preserve the same route. No row remains from which to read a stochastic model, quotient codon semantics, or an unrestricted closure oracle.
\end{proof}

\falsifiablePrediction{An accepted $\WobbleSaturationSealUp$ consumer that exposes the $f_{3}$ saturation seal without first displaying CodonSixBitWindow, DnaWindowSixBoundaryTile, SixBoundaryTileCoverage, WobbleQuotientSpectralTrigger, RadialWobbleSpectrum, hsame, Cont, Pkg, and local NameCert rows refutes the carrier surface.}

\independenceWitness{codon-six-bit-window, dna-window-six-boundary-tile, six-boundary-tile-coverage, wobble-quotient-spectral-trigger, radial-wobble-spectrum: $\WobbleSaturationSealUp$ is not bijective to any listed sibling because it jointly carries six-bit window, boundary-tile, coverage, quotient-trigger, radial-spectrum, unique $f_{3}$ saturation, terminal $\mathrm{ACG}$ seal, transport, replay, provenance, and local naming rows.}

The Lean TasteGate route for $\WobbleSaturationSealUp$ must provide explicit $\Nontrivial\ \WobbleSaturationSealUp$ and $\FieldFaithful\ \WobbleSaturationSealUp$ instances preserving $W,T,C,Q,R,D,A,H,K,P,N$ as distinguishable fields.

\closureat{WobbleSaturationSealUp}{seedStr}

\begin{closurestatus}{\WobbleSaturationSealUp}
  \constructivestory{A $\WobbleSaturationSealUp$ packet is generated from six-bit codon windows, boundary-tile rows, six-boundary coverage, quotient spectral trigger rows, radial wobble-spectrum rows, a unique f3 saturation direction, the ACG seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:wobble-saturation-seal-carrier}, \autoref{thm:wobble-saturation-seal-namecert-obligations}, and \autoref{thm:wobble-saturation-seal-nonescape} seed the finite NameCert seal for the unique $f_{3}$ directional saturation route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological stochastic dynamics, quotient codon semantics, unrestricted support closure, Lean verification, bridge checking, or saturation beyond the displayed f3 route.}
  \upgradepath{Obligation closure requires checked carrier admission, six-bit window alignment, boundary-tile coverage, quotient-trigger exactness, radial-spectrum compatibility, unique f3 saturation, ACG sealing, Nontrivial WobbleSaturationSealUp, and FieldFaithful WobbleSaturationSealUp for BEDC.Derived.WobbleSaturationSealUp.}
\end{closurestatus}
