\chapter{A Concrete Naming Certificate for $\HilbertAlexanderBlockerUp$}
\label{ch:concrete-instances-hilbert-alexander-blocker-namecert}
\origin{ai}

The $\HilbertAlexanderBlockerUp$ packet realizes the Hilbert-series blocker complex of \autoref{thm:philosophy-blocker-hilbert-series} as finite BEDC NameCert data. It sits after the simplicial-complex carrier of \autoref{ch:concrete-instances-simplicialcomplex-namecert}, the polynomial carrier of \autoref{ch:concrete-instances-polynomial-namecert}, the finite-trace evaluator surface of \autoref{ch:concrete-instances-finitetraceevaluator-namecert}, the DNA boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, and the arity-ten $\BHist$ tuple capstone of \autoref{ch:concrete-instances-b-hist-deca-tuple-name-cert-namecert}. The packet names blocker-cover, face-polynomial, Hilbert-row, Alexander-dual, and non-Cohen--Macaulay rows as displayed finite data; it is not a host Stanley--Reisner algebra oracle, a biological stochastic model, quotient codon semantics, or an unrestricted homology computation.

\begin{definition}[HilbertAlexanderBlocker carrier]
\label{def:hilbert-alexander-blocker-carrier}
A $\HilbertAlexanderBlockerUp$ carrier is a finite $\BHist$ packet
$$
H=(S,P,T,B,F,L,A,R,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SimplicialComplexUp$ row for the blocker complex and its four omitted-coordinate cover faces.
\item $P$ is the $\PolynomialUp$ row recording the face polynomial and the Hilbert numerator polynomial.
\item $T$ is the $\FiniteTraceEvaluatorUp$ row that evaluates the finite inclusion-exclusion table for cover intersections.
\item $B$ is the $\DnaWindowSixBoundaryTileUp$ row carrying the six-window boundary source and trigger coordinates.
\item $F$ is the blocker-cover row, recording the four facets and the intersection multiplicities $4,6,4,1$.
\item $L$ is the Hilbert-row ledger, recording the rational-function denominator powers $14,6,2,0$ and the signed inclusion-exclusion coefficients.
\item $A$ is the Alexander-dual row, recording the four generator complements and their lcm-degree ledger.
\item $R$ records componentwise $\hsame$ transport for $S,P,T,B,F,L,A$.
\item $C$ records displayed $\Cont$ replay from boundary-tile reads through blocker cover, face polynomial, Hilbert rows, and Alexander-dual rows.
\item $Q$ is the $\Pkg$ provenance over $\HilbertAlexanderBlockerUp$, $\SimplicialComplexUp$, $\PolynomialUp$, $\FiniteTraceEvaluatorUp$, $\DnaWindowSixBoundaryTileUp$, $\BHistDecaTupleNameCertUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HilbertAlexanderBlockerUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It has no coordinate for an ambient polynomial-ring equality oracle, an unrestricted minimal resolution, stochastic biological semantics, quotient codon equality, hidden homology computation, or external Cohen--Macaulay decision procedure.
\end{definition}

\begin{theorem}[HilbertAlexanderBlocker NameCert obligations]
\label{thm:hilbert-alexander-blocker-namecert-obligations}
For every accepted $\HilbertAlexanderBlockerUp$ carrier $H=(S,P,T,B,F,L,A,R,C,Q,N)$, the local $\NameCert_{\HilbertAlexanderBlockerUp}$ surface consists exactly of simplicial-complex admission through $S$, polynomial-row admission through $P$, finite trace evaluation through $T$, DNA boundary-tile source admission through $B$, blocker-cover exactness through $F$, Hilbert-row readback through $L$, Alexander-dual ledger exposure through $A$, componentwise $\hsame$ transport through $R$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $Q$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hilbert-alexander-blocker-carrier}. The rows $S,P,T,B,F,L,A,R,C,Q,N$ are the full accepted inventory.

The blocker-cover side is finite. The row $B$ supplies the boundary-tile source, $S$ supplies the simplicial-complex carrier, and $F$ records the four cover facets together with their intersection multiplicities.

The Hilbert side is finite as well. The row $T$ evaluates the inclusion-exclusion table, $P$ stores the face and numerator polynomials, and $L$ stores the denominator powers and signs of the Hilbert-series row.

The Alexander-dual row $A$ records the generator-complement ledger attached to the same blocker cover. The structural rows $R,C,Q,N$ transport, replay, source, and name exactly this packet, so no accepted NameCert obligation can project an ambient polynomial-ring oracle, unrestricted resolution, stochastic model, quotient codon equality, hidden homology computation, or external Cohen--Macaulay decision.
\end{proof}

\begin{theorem}[HilbertAlexanderBlocker finite Hilbert row]
\label{thm:hilbert-alexander-blocker-finite-hilbert-row}
Every Hilbert-series read from an accepted $\HilbertAlexanderBlockerUp$ packet factors through the finite route
$$
\SimplicialComplexUp,\ \PolynomialUp,\ \FiniteTraceEvaluatorUp,\ \DnaWindowSixBoundaryTileUp,\ \BHistDecaTupleNameCertUp
\longmapsto
F,L,A,R,C,Q,N .
$$
The read first displays the blocker cover and intersection table, then evaluates the face-polynomial and Hilbert-row ledger, and only then exposes Alexander-dual and local naming rows. It exports no ambient Stanley--Reisner algebra oracle, unrestricted minimal resolution, quotient codon equality, hidden homology computation, or biological stochastic model.
\end{theorem}
\begin{proof}
Apply \autoref{thm:hilbert-alexander-blocker-namecert-obligations}. It places the simplicial-complex, polynomial, trace-evaluation, and boundary-tile sources before the blocker-cover and Hilbert-row ledgers.

The finite trace row $T$ evaluates only the displayed intersection table $F$. The polynomial row $P$ and Hilbert ledger $L$ therefore read the same finite cover data rather than a host polynomial-ring quotient.

The Alexander-dual row $A$ is downstream of the same cover. Transport, replay, provenance, and local naming through $R,C,Q,N$ preserve that route, so the Hilbert-series read remains a finite NameCert packet.
\end{proof}

\falsifiablePrediction{Changing the blocker-cover multiplicity row $F$ changes the Hilbert denominator-power ledger $L$ before any accepted $\HilbertAlexanderBlockerUp$ consumer can preserve the displayed Hilbert series.}

\independenceWitness{simplicialcomplex, polynomial, finite-trace-evaluator, dna-window-six-boundary-tile, b-hist-deca-tuple-name-cert: $\HilbertAlexanderBlockerUp$ is not bijective to any listed sibling because it jointly carries blocker-cover rows, face-polynomial rows, Hilbert-series rows, Alexander-dual rows, finite trace evaluation, transport, replay, provenance, and local naming.}

\closureat{HilbertAlexanderBlockerUp}{seedStr}

\begin{closurestatus}{\HilbertAlexanderBlockerUp}
  \constructivestory{A $\HilbertAlexanderBlockerUp$ packet is generated from a SimplicialComplexUp blocker complex, PolynomialUp face and numerator rows, FiniteTraceEvaluatorUp inclusion-exclusion evaluation, DnaWindowSixBoundaryTileUp source rows, blocker-cover data, Hilbert-row ledgers, Alexander-dual ledgers, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hilbert-alexander-blocker-carrier}, \autoref{thm:hilbert-alexander-blocker-namecert-obligations}, and \autoref{thm:hilbert-alexander-blocker-finite-hilbert-row} seed the finite Hilbert-series blocker packet over cover, polynomial, trace-evaluation, boundary-tile, and tuple-name rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, host Stanley--Reisner algebra equality, unrestricted minimal resolutions, stochastic biological semantics, quotient codon equality, hidden homology computation, or external Cohen--Macaulay decision.}
  \upgradepath{Obligation closure requires checked carrier admission, blocker-cover exactness, face-polynomial readback, Hilbert-row ledger exactness, Alexander-dual ledger exposure, trace-evaluation stability, transport, replay, provenance, and local naming for BEDC.Derived.HilbertAlexanderBlockerUp.}
\end{closurestatus}
