\chapter{A Concrete Naming Certificate for $\DiagonalSequenceUp$}
\label{ch:concrete-instances-diagonal-sequence-namecert}
\origin{human}

Following Cantor and Bishop--Bridges constructive analysis, the $\DiagonalSequenceUp$ packet records the finite diagonal-sequence surface used by Real-facing diagonal arguments. It sits over the stream-row discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic bit ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. It is consumed downstream by \autoref{ch:concrete-instances-real-diagonal-non-surjection-namecert} and \autoref{ch:concrete-instances-cantor-diagonal-real-uncountability-namecert}. The packet names the reusable diagonal schedule and readback route; it is not a host countability theorem, a quotient-stream principle, or a completed powerset construction.

\begin{definition}[Diagonal sequence carrier]
\label{def:diagonal-sequence-carrier}
A $\DiagonalSequenceUp$ carrier is a finite $\BHist$ packet
$$
D=(E,W,B,F,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the inspected enumeration surface, exposing only finite $\StreamNameUp$ candidate windows.
\item $W$ is the diagonal schedule row, pairing each inspected enumeration row with the coordinate at which the diagonal value is read.
\item $B$ is the dyadic observation row, read through $\DyadicRatCoreUp$ before any regular rational or Real-facing seal is exposed.
\item $F$ is the finite flip row, assigning the displayed opposite dyadic value at each scheduled coordinate.
\item $Q$ is the $\RegSeqRatUp$ readback row generated from the same schedule and flip ledger.
\item $R$ is the terminal $\RealUp$ seal row, downstream of $E,W,B,F,Q$.
\item $H$ records componentwise $\hsame$ transport for enumeration, schedule, dyadic observation, flip, regular readback, Real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an enumeration request through the scheduled dyadic read, flip, regular readback, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\DiagonalSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DiagonalSequenceUp}$ row.
\end{enumerate}
The classifier accepts a packet only when the diagonal schedule is finite, the dyadic observation and flip rows share the same coordinate ledger, the regular readback reuses that ledger, and the Real seal is downstream of the displayed readback route.
\end{definition}

\begin{theorem}[Diagonal sequence NameCert obligations]
\label{thm:diagonal-sequence-namecert-obligations}
For every accepted $\DiagonalSequenceUp$ carrier $D=(E,W,B,F,Q,R,H,C,P,N)$, the local $\NameCert_{\DiagonalSequenceUp}$ surface consists exactly of enumeration-window admission through $E$, finite diagonal scheduling through $W$, dyadic observation through $B$, flip exactness through $F$, regular rational readback through $Q$, Real sealing through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:diagonal-sequence-carrier}. The displayed inventory is exactly $E,W,B,F,Q,R,H,C,P,N$.

Read the construction rows in order. The enumeration surface $E$ is inspected only along the finite schedule $W$, the dyadic observation $B$ is made at those scheduled coordinates, and the flip row $F$ assigns the opposite displayed dyadic value on the same ledger.

The readback rows are downstream. The row $Q$ records regular rational readback from the scheduled flip ledger, while $R$ seals the resulting sequence as $\RealUp$ data. Componentwise transport, displayed replay, provenance, and naming preserve those rows and introduce no extra coordinate. Hence the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Diagonal sequence nonescape]
\label{thm:diagonal-sequence-nonescape}
Every accepted $\DiagonalSequenceUp$ consumer must read the finite route
$$
\StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp
$$
through the displayed schedule $W$ and flip ledger $F$ before it can expose a diagonal Real-facing value. The packet exports no host enumeration principle, quotient stream equality, unbounded choice of coordinates, powerset of reals, or completed uncountability theorem.
\end{theorem}
\begin{proof}
Use \autoref{thm:diagonal-sequence-namecert-obligations}. It orders the inspected stream windows, dyadic observations, flip ledger, regular readback, and Real seal inside one finite carrier.

The nonescape clauses follow from the absence of any other carrier coordinate. The rows $H,C,P,N$ can transport, replay, source, and name the displayed route, but they cannot add a host enumeration theorem or a quotient equality principle. Thus every downstream diagonal packet must consume the same finite sequence route rather than bypass it.
\end{proof}

\closureat{DiagonalSequenceUp}{seedStr}

\begin{closurestatus}{\DiagonalSequenceUp}
  \constructivestory{A $\DiagonalSequenceUp$ packet is generated from finite StreamName windows, a diagonal schedule, DyadicRatCore observations, a flip ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:diagonal-sequence-carrier}, \autoref{thm:diagonal-sequence-namecert-obligations}, and \autoref{thm:diagonal-sequence-nonescape} seed the reusable finite diagonal-sequence packet consumed by Real-facing diagonal arguments.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host countability, quotient stream equality, unbounded coordinate choice, powerset constructions, Real uncountability, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, schedule exactness, dyadic flip compatibility, regular readback, Real sealing, provenance exhaustion, and local naming for BEDC.Derived.DiagonalSequenceUp.}
\end{closurestatus}
