\chapter{A Concrete Naming Certificate for $\FormalBallBasisUp$}
\label{ch:concrete-instances-formal-ball-basis-namecert}
\origin{human}

Bishop-style constructive metric-basis language presents completion data through located balls, positive rational radii, and finite cover-refinement witnesses before any quotient of Cauchy names is read. The $\FormalBallBasisUp$ packet records that basis-level substrate between the metric surface of \autoref{ch:concrete-instances-metric-namecert}, the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the formal-ball packet of \autoref{ch:concrete-instances-formalball-namecert}, and the metric-completion route of \autoref{ch:concrete-instances-metriccompletion-namecert}. It is a finite source for L10 completion and Cauchy-filter consumers, not an open-cover compactness theorem, not a quotient-ball construction, and not an ambient completeness principle.

\begin{definition}[Formal-ball basis carrier]
\label{def:formal-ball-basis-carrier}
A $\FormalBallBasisUp$ carrier is a finite $\BHist$ packet
$$
B=(X,d,c,r,I,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricSpaceUp$ carrier row that supplies the inspected points and distance requests.
\item $d$ is the metric-distance ledger read through the same $\MetricSpaceUp$ surface.
\item $c$ is the finite centre schedule, listing the displayed centres used by the basis rows.
\item $r$ is the positive radius ledger over $\DyadicRatCoreUp$ and $\RealUp$, recording dyadic tolerances and their terminal real-name seals.
\item $I$ is the incidence row recording which displayed point requests enter which formal balls.
\item $R$ is the refinement row, recording finite ball-containment and radius-shrink requests over $\FormalBallUp$ before any completion consumer is reached.
\item $H$ records componentwise $\hsame$ transport for the metric, centre, radius, incidence, refinement, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from metric requests through centres, radii, formal-ball incidence, refinement, and completion-facing handoff.
\item $P$ is the $\Pkg$ provenance over $\MetricSpaceUp$, $\DyadicRatCoreUp$, $\RealUp$, $\FormalBallUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FormalBallBasisUp}$ row.
\end{enumerate}
The carrier has no coordinate for open-cover compactness, quotient balls, selected centres beyond $c$, selected Cauchy limits, or ambient completeness.
\end{definition}

\begin{theorem}[Formal-ball basis NameCert obligations]
\label{thm:formal-ball-basis-namecert-obligations}
For an accepted $\FormalBallBasisUp$ carrier
$$
B=(X,d,c,r,I,R,H,C,P,N),
$$
the local $\NameCert_{\FormalBallBasisUp}$ surface consists exactly of carrier admission, metric-row exposure through $X,d$, centre-schedule exposure through $c$, positive-radius exposure through $r$, formal-ball incidence through $I$, finite refinement through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$. Every basis read is exhausted by these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:formal-ball-basis-carrier}. The displayed rows are exactly the metric carrier, metric ledger, centre schedule, radius ledger, incidence row, refinement row, transport row, replay row, provenance row, and local name.

The metric and radius rows supply the source data. The row $X$ provides the inspected metric points and $d$ provides the finite distance requests, while $r$ records only dyadic and real-name radius data.

The formal-ball rows are then $I$ and $R$. Incidence and refinement are read after the centres and radii have been displayed, so no consumer can substitute quotient balls or a selected completion point for the basis rows.

Finally $H,C,P,N$ preserve, replay, source, and name the same finite packet. Since the carrier has no other coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Formal-ball basis metric-completion handoff]
\label{thm:formal-ball-basis-metric-completion-handoff}
Every $\MetricCompletionUp$ consumer of an accepted $\FormalBallBasisUp$ packet must read the displayed route
$$
X,d \longmapsto c,r \longmapsto I,R \longmapsto H,C,P,N
$$
before completion data is available. Thus the completion handoff sees a finite basis of metric centres, dyadic and real radii, formal-ball incidence, and formal-ball refinement, and it receives no quotient ball carrier, selected Cauchy limit, open-cover compactness witness, selected centre outside $c$, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:formal-ball-basis-namecert-obligations}. They force every consumer to read the metric rows $X,d$, the centre and radius rows $c,r$, and the formal-ball rows $I,R$ before any structural row is used.

The provenance row names $\MetricCompletionUp$ only as a downstream consumer of the same route. Therefore completion-facing reads inherit the displayed formal-ball basis rather than a quotient of Cauchy names or a host completion object.

Transport and replay through $H$ and $C$ preserve the route, while $P$ and $N$ only source and name it. The excluded compactness, quotient-ball, selected-centre, selected-limit, and ambient-completeness objects are absent from the carrier.
\end{proof}

\begin{theorem}[Formal-ball basis Cauchy-filter refinement]
\label{thm:formal-ball-basis-cauchy-filter-refinement}
Every $\CauchyFilterUp$ or $\CauchyFilterCompletionUp$ consumer of an accepted $\FormalBallBasisUp$ packet must read the metric row $X,d$, the centre schedule $c$, the dyadic and real radius ledger $r$, the incidence row $I$, and the refinement row $R$ before completion-facing data is available. The consumer route factors through $\FormalBallUp$ and $\MetricCompletionUp$ using only $H,C,P,N$ for transport, replay, provenance, and local naming, and it receives no quotient filter, selected limit, countable-choice schedule, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the accepted carrier $B=(X,d,c,r,I,R,H,C,P,N)$ of \autoref{def:formal-ball-basis-carrier}. The NameCert obligations of \autoref{thm:formal-ball-basis-namecert-obligations} expose the metric row, centre schedule, radius ledger, incidence row, and finite refinement row as the whole basis surface.

The Cauchy-filter consumer therefore starts from the same displayed ball data as the metric-completion consumer. The formal-ball incidence row $I$ names the inspected balls, and the refinement row $R$ supplies the finite containment and radius-shrink reads before any completion-facing handoff can be consumed.

Now route through the existing handoff of \autoref{thm:formal-ball-basis-metric-completion-handoff}. The rows $H,C,P,N$ preserve and name the route from metric data through $\FormalBallUp$ into $\MetricCompletionUp$, so a $\CauchyFilterUp$ or $\CauchyFilterCompletionUp$ reader receives the finite formal-ball refinement corridor rather than a quotient filter or a chosen limit.

Since the carrier has no coordinate for quotient filters, selected Cauchy limits, countable choice, or ambient completeness, those objects cannot be exported by the refinement read.
\end{proof}

\falsifiablePrediction{If a completion-facing read uses a formal-ball basis without displaying the metric row, centre schedule, dyadic or real radius ledger, incidence row, and refinement row, it is not a $\FormalBallBasisUp$ packet.}

\independenceWitness{Nearest siblings: formalball, metriccompletion, bishopregularcauchycompletion, cauchyfiltercompletioncriterion, dyadicratcore; FormalBallBasisUp is not bijective to them because it binds a finite centre-radius basis and refinement row between metric balls and completion consumers.}

\closureat{FormalBallBasisUp}{seedStr}

\begin{closurestatus}{\FormalBallBasisUp}
  \constructivestory{A $\FormalBallBasisUp$ packet is generated from a displayed MetricSpace row, metric-distance ledger, finite centre schedule, DyadicRatCore and Real radius rows, FormalBall incidence, finite refinement, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:formal-ball-basis-carrier}, \autoref{thm:formal-ball-basis-namecert-obligations}, and \autoref{thm:formal-ball-basis-metric-completion-handoff} seed the finite basis-level substrate between formal balls and metric completion.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, quotient balls, selected centres beyond the displayed rows, selected Cauchy limits, or ambient completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, centre and radius visibility, formal-ball incidence, refinement transport, replay stability, and metric-completion handoff non-escape for BEDC.Derived.FormalBallBasisUp.}
\end{closurestatus}
