\chapter{A Concrete Naming Certificate for $\SierpinskiCarpetUp$}
\label{ch:concrete-instances-sierpinski-carpet-namecert}
\origin{human}

Following Sierpinski and the constructive compact-metric treatment of finite square approximations, the $\SierpinskiCarpetUp$ packet records the standard middle-square deletion fractal as retained grid rows and coordinate readback data. It sits beside the retained-prefix route of \autoref{ch:concrete-instances-cantorset-namecert}, the compact source discipline of \autoref{ch:concrete-instances-compactmetric-namecert}, the finite-grid continuous-surjection surface of \autoref{ch:concrete-instances-peano-curve-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet names only finite square-grid retention and coordinate windows; it does not import a host closed subset of the plane, an infinite branch selector, quotient equality of real pairs, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Sierpinski carpet carrier]
\label{def:sierpinski-carpet-carrier}
A $\SierpinskiCarpetUp$ carrier is a finite $\BHist$ packet
$$
S=(G,D,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the retained square-grid row. It records a finite triadic square address, its depth, the retained child squares at that depth, and the compact-metric grid enclosure used by later consumers.
\item $D$ is the deleted-middle-square ledger. For every inspected square address it records whether the central child has been removed and which retained children remain available.
\item $W$ is the coordinate $\StreamNameUp$ window row, carrying the finite horizontal and vertical coordinate windows attached to the retained square.
\item $Q$ is the $\RegSeqRatUp$ readback row for the two coordinate schedules, with dyadic comparisons routed through $\DyadicRatCoreUp$ before any real seal is exposed.
\item $E$ is the pair of $\RealUp$ coordinate seals obtained from the same retained square-grid and coordinate-window rows.
\item $H$ records componentwise $\hsame$ transport for retained grid rows, deletion ledgers, coordinate windows, rational readbacks, real seals, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route from retained grid rows and deleted-middle-square ledgers through coordinate windows, rational readbacks, and real seals.
\item $P$ is the $\Pkg$ provenance over $\SierpinskiCarpetUp$, $\CantorSetUp$, $\CompactMetricUp$, $\PeanoCurveUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SierpinskiCarpetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $G,D,W,Q,E,H,C,P,N$. It has no coordinate for a completed planar subset, selected infinite address, quotient equality of real pairs, open-cover compactness, or ambient completeness.
\end{definition}

\begin{theorem}[Sierpinski carpet NameCert obligations]
\label{thm:sierpinski-carpet-namecert-obligations}
For every accepted $\SierpinskiCarpetUp$ carrier
$$
S=(G,D,W,Q,E,H,C,P,N),
$$
the local $\NameCert_{\SierpinskiCarpetUp}$ surface consists exactly of carrier admission for the displayed packet; retained square-grid exposure through $G$; deleted-middle-square exclusion through $D$; coordinate window exposure through $W$; regular rational readback through $Q$; real coordinate sealing through $E$; componentwise transport through $H$; displayed replay through $C$; provenance through $P$; and local naming through $N$. No obligation is discharged by a host planar powerset, an infinite branch selector, quotient real-pair equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:sierpinski-carpet-carrier}. The accepted packet displays exactly the retained square-grid row, deletion ledger, coordinate windows, rational readbacks, real seals, and structural rows.

The retained-grid and deletion obligations are exhausted by $G$ and $D$. A consumer cannot inspect a square address until the retained child row has been displayed, and a deleted central square can be refused only by the ledger row attached to that same address.

The coordinate obligations are exhausted by $W,Q,E$. The coordinate windows are read first, the regular rational readback uses those windows with the dyadic tolerance ledger, and the $\RealUp$ seals remain downstream of the same retained square.

Finally $H,C,P,N$ transport, replay, source, and name only the displayed rows. Since the excluded host principles have no carrier coordinate, they cannot appear as local $\NameCert_{\SierpinskiCarpetUp}$ obligations.
\end{proof}

\begin{theorem}[Sierpinski carpet finite square-deletion route]
\label{thm:sierpinski-carpet-finite-square-deletion-route}
Every accepted $\SierpinskiCarpetUp$ consumer factors its membership or compact-metric read through the finite route
$$
\CantorSetUp,\CompactMetricUp,\PeanoCurveUp \longmapsto G,D \longmapsto W,Q,E \longmapsto H,C,P,N .
$$
At each inspected depth the route first displays retained square-grid rows and deleted-middle-square ledgers, then reads coordinate $\StreamNameUp$ windows, $\RegSeqRatUp$ schedules, $\DyadicRatCoreUp$ tolerances, and terminal $\RealUp$ seals. It exports no completed planar subset, selected infinite branch, quotient real-pair equality, open-cover compactness theorem, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with the retained square-grid row. It gives a finite triadic square address and the retained children available at the inspected depth, while the deleted-middle-square ledger records which central cell is refused.

Read coordinates only after that ledger is visible. The window row $W$ supplies the horizontal and vertical finite schedules, and $Q$ reads those schedules as regular rational data with the dyadic tolerance comparisons already displayed.

The Real-facing boundary is then the row $E$. It seals the two coordinate schedules as $\RealUp$ data for the retained square already named by $G$ and checked by $D$.

The structural rows preserve the same route. Componentwise transport, displayed replay, provenance, and local naming cannot create a second membership surface, so every compact-metric or coordinate consumer remains inside the finite square-deletion packet.
\end{proof}

\closureat{SierpinskiCarpetUp}{seedStr}

\begin{closurestatus}{\SierpinskiCarpetUp}
  \constructivestory{A $\SierpinskiCarpetUp$ packet is generated from retained square-grid rows, deleted-middle-square ledgers, coordinate StreamName windows, RegSeqRat readbacks, DyadicRatCore tolerance checks, RealUp coordinate seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sierpinski-carpet-carrier}, \autoref{thm:sierpinski-carpet-namecert-obligations}, and \autoref{thm:sierpinski-carpet-finite-square-deletion-route} seed the finite square-deletion compact-metric certificate surface for the Sierpinski carpet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host planar powersets, selected infinite addresses, quotient equality of real coordinate pairs, open-cover compactness, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, retained square-grid exposure, deleted-middle-square exclusion, coordinate readback, Real coordinate sealing, transport, replay, provenance, and local naming for BEDC.Derived.SierpinskiCarpetUp.}
\end{closurestatus}
