\chapter{A Concrete Naming Certificate for $\SubordinateFiniteModulusCoverUp$}
\label{ch:concrete-instances-subordinate-finite-modulus-cover-namecert}
\origin{human}

Following Lebesgue-number and Bishop--Bridges compact-uniform-continuity arguments, the $\SubordinateFiniteModulusCoverUp$ packet records the finite subordinate cover that feeds the uniform-modulus fold in \autoref{ch:visions-compact-uniform-continuity}. It sits over the compact finite-net carrier of \autoref{ch:concrete-instances-compactmetric-namecert}, the pointwise map ledger of \autoref{ch:concrete-instances-continuousmap-namecert}, the positive-radius lower-bound surface of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, and the downstream uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet names only the finite cover rows, pointwise modulus rows, rational fold ledger, transport, replay, provenance, and local naming data; it does not export open-cover compactness, a selected infinite subcover, host minima, quotient real equality, or an external semantic modulus.

\begin{definition}[Subordinate finite modulus cover carrier]
\label{def:subordinate-finite-modulus-cover-carrier}
A $\SubordinateFiniteModulusCoverUp$ carrier is a finite $\BHist$ packet
$$
C=(K,F,L,Q,U,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ finite-net row, naming the centers and the source-distance coverage windows inspected by the packet.
\item $F$ is the $\ContinuousMapUp$ pointwise-modulus row, assigning a local modulus window to each displayed center.
\item $L$ is the $\FiniteLebesgueNumberUp$ subordinate-radius row, recording a positive radius below the cover radius for each displayed local modulus.
\item $Q$ is the $\RatUp$ fold row that computes the finite lower-bound tolerance from the displayed subordinate radii.
\item $U$ is the $\UniformModulusUp$ handoff row, exposed only after $K,F,L,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $K,F,L,Q,U$ and for the replay, provenance, and local naming rows.
\item $R$ records displayed $\Cont$ replay from compact-net inspection through pointwise modulus rows, subordinate radii, rational folding, and uniform-modulus handoff.
\item $P$ is the $\Pkg$ provenance over $\SubordinateFiniteModulusCoverUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\FiniteLebesgueNumberUp$, $\RatUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SubordinateFiniteModulusCoverUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,F,L,Q,U,H,R,P,N$. The carrier has no coordinate for open-cover compactness, infinite subcover selection, host minimum extraction, quotient equality of real radii, ambient completeness, Lean verification, or bridge credentials.
\end{definition}

\begin{theorem}[Subordinate finite modulus cover NameCert obligations]
\label{thm:subordinate-finite-modulus-cover-namecert-obligations}
For every accepted $\SubordinateFiniteModulusCoverUp$ carrier $C=(K,F,L,Q,U,H,R,P,N)$, the local $\NameCert_{\SubordinateFiniteModulusCoverUp}$ surface consists exactly of compact-net admission through $K$, pointwise-modulus admission through $F$, subordinate positive-radius exposure through $L$, finite rational lower-bound folding through $Q$, uniform-modulus handoff through $U$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $R$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:subordinate-finite-modulus-cover-carrier}. The analytic rows are the compact-net row $K$, the pointwise-modulus row $F$, the subordinate-radius row $L$, the rational fold $Q$, and the uniform-modulus handoff $U$.

The compact row $K$ supplies only a finite bundle of centers and source-distance windows. The continuous-map row $F$ is read at those displayed centers, and $L$ records the positive subordinate radius attached to each local modulus row.

The fold row $Q$ is a finite $\RatUp$ computation over the displayed subordinate radii. It is not a host minimum over an open cover and cannot select an infinite subcover or appeal to quotient equality of real radii.

Finally $U,H,R,P,N$ export, transport, replay, source, and name the same finite packet. Since the carrier contains no coordinate for open-cover compactness, infinite subcover choice, host minima, quotient real equality, ambient completeness, Lean verification, or bridge checking, the listed rows exhaust the local NameCert obligations.
\end{proof}

\closureat{SubordinateFiniteModulusCoverUp}{seedStr}

\begin{closurestatus}{\SubordinateFiniteModulusCoverUp}
  \constructivestory{A $\SubordinateFiniteModulusCoverUp$ packet is generated from CompactMetric finite-net rows, ContinuousMap pointwise-modulus rows, FiniteLebesgueNumber subordinate-radius rows, RatUp lower-bound folds, a UniformModulus handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:subordinate-finite-modulus-cover-carrier} and \autoref{thm:subordinate-finite-modulus-cover-namecert-obligations} seed the subordinate finite-cover carrier consumed by compact-uniform-continuity routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, infinite subcover selection, host minimum extraction, quotient equality of real radii, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-net exposure, pointwise-modulus admission, subordinate-radius exactness, rational lower-bound folding, UniformModulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.SubordinateFiniteModulusCoverUp.}
\end{closurestatus}
