\chapter{A Concrete Naming Certificate for $\BishopRealLocatedOrderUp$}
\label{ch:concrete-instances-bishop-real-located-order-namecert}
\origin{human}

Following Bishop and Bridges on constructive real numbers and located order, the $\BishopRealLocatedOrderUp$ packet records the order-facing interface needed by L10 real and completion consumers. It sits between the Bishop real packet of \autoref{ch:concrete-instances-bishopreal-namecert}, the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, the dyadic readback of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the Archimedean real interface of \autoref{ch:concrete-instances-archimedeanreal-namecert}. The packet supplies displayed located-order and apartness rows for RealAlgOrder, monotone convergence, and completion-facing handoffs; it does not assert trichotomy, quotient real equality, host equality, selected suprema, or ambient completeness.

\begin{definition}[Bishop real located order carrier]
\label{def:bishop-real-located-order-carrier}
A $\BishopRealLocatedOrderUp$ carrier is a finite $\BHist$ packet
$$
L=(B,R,D,S,Q,A,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BishopRealUp$ source row, exposing the regular-Cauchy real name and its Bishop apartness interface.
\item $R$ is the terminal $\RealUp$ seal reached only after the Bishop source and its readback rows have been displayed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and comparison row used for rational bracketing.
\item $S$ is the $\StreamNameUp$ window row through which finite name observations are requested.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the displayed windows and dyadic tolerances.
\item $A$ is the apartness-stability row, recording that positive rational separation is transported through the same finite readback route.
\item $O$ is the located-order row, recording finite lower-or-upper rational alternatives only as displayed order evidence.
\item $H$ records componentwise $\hsame$ transport for the Bishop source, Real seal, dyadic row, stream windows, regular readback, apartness row, located-order row, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from Bishop source inspection through stream windows, dyadic tolerance, regular readback, apartness, located-order evidence, and Real sealing.
\item $P$ is the $\Pkg$ provenance over $\BishopRealLocatedOrderUp$, $\BishopRealUp$, $\RealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\ArchimedeanRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopRealLocatedOrderUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,R,D,S,Q,A,O,H,C,P,N$. It has no coordinate for trichotomy, quotient real equality, host equality, selected suprema, a least-upper-bound operator, or ambient completeness.
\end{definition}

\begin{theorem}[Bishop real located order NameCert obligations]
\label{thm:bishop-real-located-order-namecert-obligations}
For every accepted $\BishopRealLocatedOrderUp$ carrier $L=(B,R,D,S,Q,A,O,H,C,P,N)$, the local $\NameCert_{\BishopRealLocatedOrderUp}$ surface consists exactly of carrier admission for the displayed rows; Bishop source exposure through $B$; Real sealing through $R$; dyadic tolerance and comparison readback through $D$; finite stream-window exposure through $S$; regular-rational readback through $Q$; apartness stability through $A$; located-order evidence through $O$; componentwise transport through $H$; displayed replay through $C$; provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-real-located-order-carrier}. The source rows are exactly $B,S,D,Q,R$, so every order-facing read begins at the Bishop real source and reaches the Real seal only through displayed stream, dyadic, and regular-rational rows.

Read the order rows next. Apartness stability is the row $A$, and located-order evidence is the row $O$; neither row contains a trichotomy decision, a quotient equality proof, a selected supremum, or a host completeness principle.

Finally inspect $H,C,P,N$. These rows transport, replay, source, and name the same finite packet. Since the refused host-level objects have no carrier coordinate, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Bishop real located order apartness stability]
\label{thm:bishop-real-located-order-apartness-stability}
Every accepted apartness read from a $\BishopRealLocatedOrderUp$ packet factors through
$$
B,S,D,Q,A,H,C,P,N
$$
before it can be consumed by a $\RealUp$ or completion-facing route. Thus positive separation is stable under the displayed $\hsame$ and $\Cont$ rows, but the read exports no quotient real equality, host equality, trichotomy, selected supremum, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the Bishop source $B$. Its apartness evidence is not read directly by a host order relation; it is exposed through the finite stream windows $S$, the dyadic tolerance row $D$, and the regular-rational readback row $Q$.

Apply the apartness row $A$. This row records positive rational separation along that same route, so the consumer may transport a displayed separation only when the source, window, dyadic, and readback rows remain attached.

Use $H$ and $C$ for classifier movement. They preserve the displayed route and do not add a quotient-equality or trichotomy coordinate. Hence every accepted apartness read remains inside $B,S,D,Q,A,H,C,P,N$.
\end{proof}

\begin{theorem}[Bishop real located order regular-sequence scope]
\label{thm:bishop-real-located-order-regular-sequence-scope}
Every regular-sequence consumer of an accepted $\BishopRealLocatedOrderUp$ packet must read the located-order interface through
$$
\BishopRealUp,\StreamNameUp,\DyadicRatCoreUp,\RegSeqRatUp,\RealUp,\ArchimedeanRealUp
$$
as displayed by $B,S,D,Q,R,O,H,C,P,N$. The exported scope is a constructive located-order handoff for RealAlgOrder, monotone convergence, and completion routes; it is not a trichotomy principle, a quotient real equality rule, a host equality rule, a selected-supremum package, or an ambient completeness assertion.
\end{theorem}
\begin{proof}
Read the regular-sequence route through $S,D,Q$. These rows expose the finite stream windows, dyadic tolerances, and regular-rational readback before the terminal Real seal $R$ can be used.

The located-order row $O$ is downstream of that route and is sourced by the Bishop real row $B$ together with the Archimedean provenance recorded in $P$. It therefore supplies order evidence only as a displayed finite handoff, not as a host-level order totality theorem.

The structural rows $H,C,N$ preserve the same scope under accepted classifier movement. Since no carrier coordinate names trichotomy, quotient equality, host equality, selected suprema, or ambient completeness, regular-sequence consumers receive only the constructive located-order handoff.
\end{proof}

\falsifiablePrediction{Every completion-facing $\BishopRealLocatedOrderUp$ read factors through displayed BishopReal, StreamName, DyadicRatCore, RegSeqRat, RealUp, apartness, located-order, transport, replay, provenance, and local naming rows before it can be used as constructive order evidence.}

\independenceWitness{bishopreal, real, dyadicratcore, streamname, regseqrat, archimedeanreal: $\BishopRealLocatedOrderUp$ is not bijective to any listed sibling because it jointly carries apartness stability and located-order evidence over the same finite Bishop real readback route.}

\closureat{BishopRealLocatedOrderUp}{seedStr}

\begin{closurestatus}{\BishopRealLocatedOrderUp}
  \constructivestory{A $\BishopRealLocatedOrderUp$ packet is generated from a BishopReal source row, RealUp seal, DyadicRatCore tolerance row, StreamName windows, RegSeqRat readback, apartness stability, located-order evidence, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-real-located-order-carrier}, \autoref{thm:bishop-real-located-order-namecert-obligations}, \autoref{thm:bishop-real-located-order-apartness-stability}, and \autoref{thm:bishop-real-located-order-regular-sequence-scope} seed the constructive located-order interface for Bishop real, regular-sequence, and completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close trichotomy, quotient real equality, host equality, selected suprema, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Lean closure requires carrier admission, NameCert obligations, apartness stability, regular-sequence scope, and TasteGate field faithfulness for BEDC.Derived.BishopRealLocatedOrderUp.}
\end{closurestatus}
