\chapter{A Concrete Naming Certificate for $\HadamardThreeLinesUp$}
\label{ch:concrete-instances-hadamard-three-lines-namecert}
\origin{human}

Following Hadamard's three-lines theorem and the Riesz-Thorin style reading of holomorphic strip estimates, the $\HadamardThreeLinesUp$ packet records a finite vertical-strip ledger whose boundary-line reads, interior height read, and logarithmic-convexity bound are all displayed before a strip-bound consumer may read an estimate. It sits beside the annular packet of \autoref{ch:concrete-instances-hadamard-three-circle-namecert}, over the holomorphic carrier of \autoref{ch:concrete-instances-holomorphic-namecert}, the complex carrier of \autoref{ch:concrete-instances-complex-namecert}, the Real seal of \autoref{ch:concrete-instances-real-namecert}, the finite integral row of \autoref{ch:concrete-instances-integral-namecert}, and the metric annulus packet of \autoref{ch:concrete-instances-metric-annulus-namecert}. The chapter names the finite strip-bound certificate only; it does not collapse strip geometry into an annulus certificate, assert host supremum selection, or add a bridge certificate.

\begin{definition}[Hadamard three-lines carrier]
\label{def:hadamard-three-lines-carrier}
A $\HadamardThreeLinesUp$ carrier is a finite $\BHist$ packet
$$
L=(S,F,Y_0,Y_1,Y,B,M,E,Hs,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the displayed vertical-strip row, exposing the two boundary lines and the inspected interior line.
\item $F$ is the $\HolomorphicUp$ map row on the strip, with values in the $\ComplexUp$ carrier.
\item $Y_0,Y_1,Y$ are the two boundary-height $\RealUp$ reads and the inspected interior-height $\RealUp$ read, ordered by the strip row before any bound is consumed.
\item $B$ is the boundary-line readback row, exposing the finite probes on the two boundary lines and the requested interior line.
\item $M$ is the finite boundary-majorant row, recording only displayed upper-bound data for the boundary reads.
\item $E$ is the logarithmic-convexity estimate row tying $Y_0,Y_1,Y$ and $M$ to a single finite strip-bound certificate.
\item $Hs$ records componentwise $\hsame$ transport for the strip row, holomorphic map row, height reads, boundary reads, majorant row, estimate row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a strip-bound request through $S,F,Y_0,Y_1,Y,B,M,E,Hs$.
\item $P$ is the $\Pkg$ provenance over $\HadamardThreeLinesUp$, $\HadamardThreeCircleUp$, $\HolomorphicUp$, $\ComplexUp$, $\RealUp$, $\IntegralUp$, $\MetricAnnulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HadamardThreeLinesUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these displayed rows. It has no coordinate for quotient function equality, a selected boundary supremum, an unbounded strip limit, countable choice, ambient Real completeness, or an annulus replacement of the strip route.
\end{definition}

\begin{theorem}[Hadamard three-lines NameCert obligations]
\label{thm:hadamard-three-lines-namecert-obligations}
For every accepted $\HadamardThreeLinesUp$ carrier $L=(S,F,Y_0,Y_1,Y,B,M,E,Hs,C,P,N)$, the local $\NameCert_{\HadamardThreeLinesUp}$ surface is exhausted by strip admission, holomorphic-map exposure, two boundary-height reads, one interior-height read, boundary-line readback, finite boundary-majorant rows, logarithmic-convexity estimate compatibility, componentwise transport, displayed replay, provenance, and local naming. A consumer of the packet may not infer quotient function equality, host function extensionality, selected boundary suprema, unbounded strip limiting, countable choice, ambient $\RealUp$ completeness, or a collapse into $\HadamardThreeCircleUp$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hadamard-three-lines-carrier}. The rows $S,F,Y_0,Y_1,Y$ display the strip, the holomorphic map, and the three height reads before an estimate can be consumed.

The boundary computation is finite. The row $B$ exposes the inspected boundary-line probes, $M$ records their finite majorant data, and $E$ binds those rows to the logarithmic-convexity estimate for the same boundary and interior heights.

Finally the structural rows $Hs,C,P,N$ transport, replay, cite provenance, and name that same finite route. Since none of these rows adds quotient function equality, host extensionality, selected suprema, an unbounded limiting principle, countable choice, ambient Real completeness, or an annulus replacement coordinate, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Hadamard three-lines strip-bound route]
\label{thm:hadamard-three-lines-strip-bound-route}
Every strip-bound consumer of an accepted $\HadamardThreeLinesUp$ carrier factors through
$$
\HolomorphicUp \longmapsto \ComplexUp \longmapsto \RealUp \longmapsto \IntegralUp
$$
together with the displayed rows $S,F,Y_0,Y_1,Y,B,M,E,Hs,C,P,N$. The route exports a finite vertical-strip ledger and its logarithmic-convexity estimate, not the annulus ledger of $\HadamardThreeCircleUp$, not a $\MetricAnnulusUp$ maximum handoff, and not an ambient analytic object outside the displayed strip.
\end{theorem}
\begin{proof}
Start from the strip row. The packet reads the displayed strip data $S$ and the $\HolomorphicUp$ map row $F$ before any boundary-line estimate is available.

Next seal the height and boundary rows. The $\RealUp$ reads $Y_0,Y_1,Y$ determine the inspected boundary and interior lines, while $B$ turns those lines into finite boundary probes.

The strip-bound handoff is then local. The row $M$ records the finite boundary majorants, and $E$ ties them to the logarithmic-convexity estimate for the same heights. The $\IntegralUp$ dependency is consumed only as a displayed finite contour, averaging, or boundary-read row, not as an ambient selection principle.

The provenance row may cite $\HadamardThreeCircleUp$ and $\MetricAnnulusUp$ as neighboring complex-analysis certificates, but the carrier keeps its strip row $S$ and height ledger $Y_0,Y_1,Y$. Therefore a consumer receives exactly the finite strip ledger and no annulus collapse, selected extremal point, quotient equality, or infinite limiting data.
\end{proof}

\falsifiablePrediction{An accepted $\HadamardThreeLinesUp$ read is refuted if the logarithmic-convexity estimate row $E$ is preserved while the displayed strip row $S$, holomorphic map row $F$, boundary and interior height reads $Y_0,Y_1,Y$, boundary-line row $B$, and finite majorant row $M$ are removed.}

\independenceWitness{hadamard-three-circle, holomorphic, complex, real, integral, metric-annulus: none is bijective with $\HadamardThreeLinesUp$ because the packet jointly carries a vertical-strip row, holomorphic map row, boundary and interior height reads, boundary-line probes, finite majorant rows, a logarithmic-convexity estimate ledger, transport, replay, provenance, and local naming.}

\closureat{HadamardThreeLinesUp}{seedStr}

\begin{closurestatus}{\HadamardThreeLinesUp}
  \constructivestory{A $\HadamardThreeLinesUp$ packet is generated from a displayed vertical strip, a holomorphic map row, two boundary-height Real reads, one interior-height Real read, boundary-line probes, finite majorant rows, a logarithmic-convexity estimate ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hadamard-three-lines-carrier}, \autoref{thm:hadamard-three-lines-namecert-obligations}, and \autoref{thm:hadamard-three-lines-strip-bound-route} seed the finite vertical-strip ledger for three-lines holomorphic strip estimates.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient function equality, host function extensionality, selected boundary suprema, unbounded strip limits, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked strip admission, holomorphic-map exposure, boundary and interior height ordering, boundary-line readback, finite majorant rows, logarithmic-convexity estimate compatibility, and structural transport for BEDC.Derived.HadamardThreeLinesUp.}
\end{closurestatus}
