\chapter{A Concrete Naming Certificate for $\UniformCauchyLimitUp$}
\label{ch:concrete-instances-uniform-cauchy-limit-namecert}
\origin{human}

Following Bishop and Bridges on uniform convergence and constructive continuity, the $\UniformCauchyLimitUp$ packet records a uniform limit of modulus-controlled real-valued continuous maps as finite NameCert data. It sits beside the continuous-map graph rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the function-specific modulus rows of \autoref{ch:concrete-instances-moduluscontinuity-namecert}, the convergence ledger of \autoref{ch:concrete-instances-real-modulus-of-convergence-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a completion-facing uniform-limit carrier without importing quotient functions, selected limits, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Uniform Cauchy limit carrier]
\label{def:uniform-cauchy-limit-carrier}
A $\UniformCauchyLimitUp$ carrier is a finite $\BHist$ packet
$$
U=(F,M,L,S,Q,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite family of $\ContinuousMapUp$ graph rows for the inspected real-valued maps.
\item $M$ is the matching family of $\ModulusContinuityUp$ rows, one for each graph row in $F$, converting target tolerances into source-window budgets.
\item $L$ is the $\RealModulusOfConvergenceUp$ ledger that records the uniform Cauchy comparison between later graph rows.
\item $S$ is the $\StreamNameUp$ window family opened at the source points and tolerance requests used by $F,M,L$.
\item $Q$ is the $\RegSeqRatUp$ readback row extracted from the displayed windows and convergence ledger.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row carrying dyadic radii, endpoint comparisons, and uniform error budgets.
\item $R$ is the terminal $\RealUp$ seal reached only after $F,M,L,S,Q,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for graph rows, modulus rows, convergence ledgers, stream windows, regular readback, dyadic tolerances, Real sealing, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a uniform tolerance request through graph inspection, modulus conversion, convergence comparison, stream-window readback, dyadic tolerance accounting, and Real sealing.
\item $P$ is the $\Pkg$ provenance over $\UniformCauchyLimitUp$, $\ContinuousMapUp$, $\ModulusContinuityUp$, $\RealModulusOfConvergenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\UniformCauchyLimitUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,M,L,S,Q,D,R,H,C,P,N$. It has no coordinate for quotient functions, selected pointwise limits, countable-choice schedules, open-cover compactness, host function equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Uniform Cauchy limit NameCert obligations]
\label{thm:uniform-cauchy-limit-namecert-obligations}
For every accepted $\UniformCauchyLimitUp$ carrier $U=(F,M,L,S,Q,D,R,H,C,P,N)$, the local $\NameCert_{\UniformCauchyLimitUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier admission for the continuous-map graph rows, modulus-continuity rows, convergence ledger, stream windows, regular rational readback, dyadic tolerance row, Real seal, transport, replay, provenance, and local naming rows;
\item graph-modulus compatibility, requiring every inspected map in $F$ to expose its matching modulus row in $M$ before a target tolerance is read;
\item uniform Cauchy exactness, requiring each later-stage comparison to pass through the displayed ledger $L$ and the dyadic tolerance row $D$;
\item readback sealing, requiring $S$ and $Q$ to be read before the terminal $\RealUp$ seal $R$ is exposed;
\item non-escape for quotient function spaces, selected limits, countable choice, open-cover compactness, host function equality, and ambient $\RealUp$ completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-cauchy-limit-carrier}. The accepted tuple displays exactly the graph rows, modulus rows, convergence ledger, windows, readback, dyadic tolerance ledger, Real seal, and structural rows.

Graph-modulus compatibility is rowwise. A consumer that reads a graph row in $F$ must read the corresponding row in $M$, so continuity is exposed as a finite tolerance-to-window route rather than as a host semantic predicate.

Uniform Cauchy exactness is the role of $L$ and $D$. Later-stage comparisons are admitted only through the displayed convergence ledger and dyadic tolerance budgets, so no hidden choice schedule or selected limit enters the packet.

Readback sealing follows through $S,Q,R$. The finite stream windows are opened first, the regular rational readback is extracted next, and the terminal Real seal is reached only after those rows are visible.

Finally, $H,C,P,N$ transport, replay, source, and name the same displayed packet. Since the refused objects are absent from the carrier, the local NameCert surface exports exactly the five obligations listed above.
\end{proof}

\begin{theorem}[Uniform Cauchy limit continuity handoff]
\label{thm:uniform-cauchy-limit-continuity-handoff}
Every continuity-facing read of an accepted $\UniformCauchyLimitUp$ packet factors through the finite route
$$
\ContinuousMapUp
\longmapsto
\ModulusContinuityUp
\longmapsto
\RealModulusOfConvergenceUp
\longmapsto
\StreamNameUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
Thus a downstream continuous-map or completion consumer receives graph rows, modulus rows, uniform convergence ledgers, finite windows, regular rational readback, dyadic tolerance accounting, componentwise transport, displayed replay, provenance, and local naming, not a quotient function or selected limit.
\end{theorem}
\begin{proof}
Project the accepted carrier $U=(F,M,L,S,Q,D,R,H,C,P,N)$. The graph rows in $F$ are the only function data, and the modulus rows in $M$ are the only continuity data attached to them.

Replay through $C$ preserves the route. A continuity-facing request first opens the graph row, then reads the displayed modulus conversion, then consults the uniform Cauchy ledger and dyadic tolerances before it can inspect stream windows and regular rational readback.

The Real seal $R$ is terminal. Since the carrier has no coordinate for quotient functions, selected limits, host equality, or ambient completeness, the handoff remains a finite BEDC route through the displayed rows.
\end{proof}

\begin{theorem}[Uniform Cauchy limit completion nonescape]
\label{thm:uniform-cauchy-limit-completion-nonescape}
Every completion-facing consumer of an accepted $\UniformCauchyLimitUp$ packet must display the rows $F,M,L,S,Q,D,R,H,C,P,N$ before reading any terminal Real seal. The accepted packet therefore supplies a uniform-limit carrier for real-valued continuous maps without exporting quotient functions, selected limit representatives, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with carrier projection. The completion-facing data are not stored in a separate ambient object; they are the displayed rows $F,M,L,S,Q,D,R,H,C,P,N$.

The finite route composes graph inspection, modulus conversion, convergence-ledger comparison, stream-window opening, regular rational readback, dyadic tolerance accounting, and terminal Real sealing. Each step is a row of the accepted carrier and is preserved by the transport and replay rows.

No refused object can be exported after the seal. Quotient functions, selected representatives, choice schedules, open-cover compactness, and ambient completeness have no carrier coordinate, so completion-facing consumers remain inside the displayed packet.
\end{proof}

\closureat{UniformCauchyLimitUp}{seedStr}

\begin{closurestatus}{\UniformCauchyLimitUp}
  \constructivestory{A $\UniformCauchyLimitUp$ packet is generated from ContinuousMap graph rows, ModulusContinuity rows, a RealModulusOfConvergence ledger, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance data, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-limit-carrier}, \autoref{thm:uniform-cauchy-limit-namecert-obligations}, \autoref{thm:uniform-cauchy-limit-continuity-handoff}, and \autoref{thm:uniform-cauchy-limit-completion-nonescape} seed the uniform-limit route over continuous-map graphs, modulus rows, convergence ledgers, finite windows, regular readback, dyadic tolerance data, and Real sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient function spaces, selected pointwise limits, countable choice, open-cover compactness, host function equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, graph-modulus compatibility, uniform Cauchy exactness, readback sealing, completion nonescape, transport, replay, provenance, and local naming for BEDC.Derived.UniformCauchyLimitUp.}
\end{closurestatus}
