\chapter{A Concrete Naming Certificate for $\MetricEntourageUp$}
\label{ch:concrete-instances-metric-entourage-namecert}
\origin{human}

Following Bourbaki uniform spaces and Bishop--Bridges constructive metric analysis, the $\MetricEntourageUp$ packet records the finite entourage surface between the metric row of \autoref{ch:concrete-instances-metric-namecert} and the uniform consumers of \autoref{ch:concrete-instances-real-uniform-space-namecert}. Its tolerance reads are grounded through \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}; it is a displayed metric-to-uniform handoff, not an open-cover compactness principle or a choice of centers.

\begin{definition}[MetricEntourage carrier]
\label{def:metric-entourage-carrier}
A $\MetricEntourageUp$ carrier is a finite $\BHist$ packet
$$
E=(M,Q,D,B,S,T,H,C,P,N).
$$
Here $M$ is the $\MetricUp$ row, $Q$ and $D$ are the rational and dyadic tolerance rows, $B$ is the ball-and-entourage witness row, $S$ is the symmetry row, $T$ is the triangle-composition row, $H$ is componentwise $\hsame$ transport, $C$ is displayed $\Cont$ replay, $P$ is $\Pkg$ provenance, and $N$ is the local $\NameCert_{\MetricEntourageUp}$ row. The carrier has no coordinate for arbitrary open covers, selected centers, quotient points, countable choice, or ambient completion.
\end{definition}

\begin{theorem}[MetricEntourage NameCert obligations]
\label{thm:metric-entourage-namecert-obligations}
For every accepted $\MetricEntourageUp$ carrier $E=(M,Q,D,B,S,T,H,C,P,N)$, the local $\NameCert_{\MetricEntourageUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the displayed metric, tolerance, entourage, symmetry, triangle, transport, replay, provenance, and local naming rows;
\item diagonal and reflexive entourage admission from the positive tolerance rows $Q,D$ and the ball witness row $B$;
\item symmetry transport through $S$ together with the componentwise $\hsame$ row $H$;
\item triangle composition through $T$, using only the displayed metric row $M$ and the rational or dyadic tolerance rows $Q,D$;
\item metric-to-uniform handoff saying that the uniform read consumes $B,S,T$ after $M,Q,D$ and before any downstream completion or Cauchy row;
\item transport and replay stability through $H,C,P,N$ for the same displayed packet; and
\item nonescape from arbitrary open covers, selected centers, quotient points, countable choice, host compactness, or ambient completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-entourage-carrier}. The only metric-facing rows are $M,Q,D,B,S,T$, and the only structural rows are $H,C,P,N$.

The diagonal and reflexive obligation reads the tolerance rows before the ball witness row. Symmetry is then supplied by $S$, and triangle composition is supplied by $T$ over the same metric and tolerance route.

The uniform handoff is therefore a finite row translation. A consumer of \autoref{ch:concrete-instances-real-uniform-space-namecert} may read the resulting entourage surface only after the metric row and tolerance rows have been displayed.

Finally the transport, replay, provenance, and naming rows preserve that route without adding any coordinate for open-cover compactness, selected centers, quotient representatives, countable choice, host compactness, or ambient completeness.
\end{proof}

\begin{closurestatus}{\MetricEntourageUp}
  \constructivestory{A $\MetricEntourageUp$ packet is generated by reading a displayed metric row, rational and dyadic tolerance rows, a ball-and-entourage witness, symmetry, triangle composition, componentwise transport, replay, provenance, and local naming. It translates metric balls into a finite uniform entourage surface without adding open-cover compactness, selected centers, quotient points, countable choice, or ambient completion.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed records the metric row, rational and dyadic tolerance rows, ball-entourage witness, symmetry, triangle-composition, transport, replay, provenance, and local NameCert rows as the current paper-side scope.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.MetricEntourageUp.MetricEntourageUp}
  \bridgestatus{none}
  \notclaimed{The chapter does not claim open-cover compactness, selected centers, quotient-point equality, countable choice, complete uniformity, or ambient metric completion.}
  \upgradepath{Next paper step: register the full MetricEntourage carrier obligation surface in Lean before raising the verification axis.}
\end{closurestatus}
