\chapter{A Concrete Naming Certificate for $\FiniteSupportRemovalUp$}
\label{ch:concrete-instances-finite-support-removal-namecert}
\origin{human}

Following Bishop and Bridges, the $\FiniteSupportRemovalUp$ packet records the constructive finite-cover operation that deletes one displayed support row while keeping the remaining finite cover, tolerance ledger, and terminal real-name route visible. It consumes the positive-radius surface of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, the compact finite-net route of \autoref{ch:concrete-instances-compact-uniform-finite-net-realization-namecert}, and the L10 dependency chain through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names a support-pruning certificate for finite compactness consumers; it is not a selected subcover functional, a host-level minimum operation, a quotient equality principle, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Finite support removal carrier]
\label{def:finite-support-removal-carrier}
A $\FiniteSupportRemovalUp$ carrier is a finite $\BHist$ packet
$$
S=(K,G,D,W,T,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact finite-net or finite-cover source row, exposing the finite list of support names and coverage witnesses.
\item $G$ is the $\FiniteLebesgueNumberUp$ positive-radius row that keeps every retained support row inside the displayed cover tolerance.
\item $D$ is the deleted support name, together with its membership witness in the original finite support spine.
\item $W$ is the retained finite window after removing $D$, with its inherited order and membership rows.
\item $T$ is the $\DyadicRatCoreUp$ tolerance ledger transported from the original cover to the retained window.
\item $R$ is the $\RegSeqRatUp$ readback row over the retained window.
\item $L$ is the terminal $\RealUp$ seal reached only through the retained $\StreamNameUp/\RegSeqRatUp/\RealUp$ route.
\item $H$ records componentwise $\hsame$ transport for $K,G,D,W,T,R,L$ and for the structural rows below.
\item $C$ records displayed $\Cont$ replay from finite-cover inspection through support deletion, tolerance transport, regular readback, and Real sealing.
\item $P$ is the $\Pkg$ provenance over $\FiniteSupportRemovalUp$, $\FiniteLebesgueNumberUp$, $\CompactUniformFiniteNetRealizationUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteSupportRemovalUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,G,D,W,T,R,L,H,C,P,N$. It has no coordinate for an undisplayed cover member, a selected replacement support, quotient equality of real names, countable choice, or an ambient compactness theorem.
\end{definition}

\begin{theorem}[Finite support removal NameCert obligations]
\label{thm:finite-support-removal-namecert-obligations}
For every accepted $\FiniteSupportRemovalUp$ carrier $S=(K,G,D,W,T,R,L,H,C,P,N)$, the local $\NameCert_{\FiniteSupportRemovalUp}$ surface consists exactly of carrier admission for the finite-cover source, positive-radius ledger, deleted support name, retained window, tolerance ledger, regular readback, Real seal, transport, replay, provenance, and local naming rows; membership exposure for $D$ in the original support spine; retained-window coverage through $W$ and $G$; L10 readback through $T,R,L$; and non-escape from selected replacement supports, quotient real equality, countable choice, and ambient compactness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-support-removal-carrier}. The rows $K,G,D,W,T,R,L,H,C,P,N$ are the complete displayed inventory.

The deletion row is finite data. Since $D$ is stored with its membership witness in the original finite support spine and $W$ stores the retained window, the packet can inspect the removed coordinate without choosing a replacement support or leaving the finite cover.

The coverage and tolerance rows are inherited only through displayed coordinates. The positive-radius row $G$ keeps the retained supports inside the finite Lebesgue-radius ledger, while $T$ transports the dyadic tolerance data to the retained StreamName window.

Finally the regular readback and Real seal are read through $R$ and $L$, then preserved by $H,C,P,N$. The refused objects are absent from the carrier, so the local NameCert surface is exactly the obligation list stated above.
\end{proof}

\begin{theorem}[Finite support removal compact-cover handoff]
\label{thm:finite-support-removal-compact-cover-handoff}
Every compactness or uniform-modulus consumer of an accepted $\FiniteSupportRemovalUp$ packet reads the deletion route through the finite chain
$$
\FiniteLebesgueNumberUp,\ \CompactUniformFiniteNetRealizationUp,\ \StreamNameUp,\ \RegSeqRatUp
\longmapsto
\RealUp .
$$
The consumer first displays the original finite support spine, then the removed coordinate and retained window, then the positive-radius and dyadic tolerance rows, and only then the regular readback and Real seal. No consumer may replace the deleted support by an undisplayed cover member, a selected subcover, quotient real equality, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:finite-support-removal-namecert-obligations}. It orders the finite-cover row, the deleted support row, the retained window, the positive-radius ledger, the tolerance ledger, the regular readback, and the terminal Real seal inside one accepted packet.

The finite cover is consumed before deletion. Thus the support spine and the deleted coordinate are both visible BEDC histories, and the retained window $W$ is a finite subspine rather than a host-level set difference.

The L10 dependency route is then forced. The retained StreamName window carries the dyadic tolerance row $T$, the regular rational readback row $R$, and the terminal $\RealUp$ seal $L$ through the same displayed route used by finite-cover compactness chapters.

Transport, replay, provenance, and local naming preserve this route without adding another support coordinate. Therefore the handoff supplies a constructive deletion primitive for compact finite-cover consumers while refusing the listed external objects.
\end{proof}

\falsifiablePrediction{An accepted $\FiniteSupportRemovalUp$ read is refuted if a compactness or uniform-modulus consumer reaches a retained Real seal without displaying the original finite support spine, the deleted support name, the retained window, the positive-radius ledger, the tolerance row, the regular readback row, transport, replay, provenance, and local naming.}

\independenceWitness{finitelebesguenumber, compactuniformfinitenetrealization, streamname, regseqrat, and real: none is bijective to the support-removal packet because only $\FiniteSupportRemovalUp$ binds a deleted finite support coordinate to a retained-window L10 readback route before the terminal $\RealUp$ seal is consumed.}

\closureat{FiniteSupportRemovalUp}{seedStr}

\begin{closurestatus}{\FiniteSupportRemovalUp}
  \constructivestory{A $\FiniteSupportRemovalUp$ packet is generated from finite-cover source rows, FiniteLebesgueNumberUp positive-radius rows, a displayed deleted support name, retained StreamName window rows, DyadicRatCoreUp tolerance rows, RegSeqRatUp readback rows, RealUp seal rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-support-removal-carrier}, \autoref{thm:finite-support-removal-namecert-obligations}, and \autoref{thm:finite-support-removal-compact-cover-handoff} seed the finite support-deletion surface for compactness and uniform-modulus consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, selected subcover extraction, quotient real equality, countable choice, host set difference, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, support membership exposure, retained-window coverage, positive-radius preservation, tolerance transport, regular readback, RealUp sealing, transport, replay, provenance, and local naming for BEDC.Derived.FiniteSupportRemovalUp.}
\end{closurestatus}
