\chapter{A Concrete Naming Certificate for $\DyadicBisectionScheduleUp$}
\label{ch:concrete-instances-dyadic-bisection-schedule-namecert}
\origin{human}

Following Bishop and Bridges constructive nested-interval and bisection arguments, the $\DyadicBisectionScheduleUp$ packet records the finite halving schedule used before a retained interval route is read as Cauchy data. It sits beside the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the located interval-zero route of \autoref{ch:concrete-instances-located-interval-bolzano-namecert}, and the retained closed-interval branch surface of \autoref{ch:concrete-instances-closed-interval-bisection-namecert}. The packet names a finite schedule object only; it does not select an infinite branch, assert an interval intersection point, or invoke ambient $\RealUp$ completeness.

\begin{definition}[Dyadic bisection schedule carrier]
\label{def:dyadic-bisection-schedule-carrier}
A $\DyadicBisectionScheduleUp$ carrier is a finite $\BHist$ packet
$$
S=(I,B,D,W,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the closed interval source row. It exposes endpoint order, containment, and the finite retained-window requests consumed from the $\ClosedIntervalBisectionUp$ route.
\item $B$ is the branch schedule row. It records the inspected finite sequence of left-or-right bisection decisions, midpoint exposure, retained-child containment, and width-halving ledger.
\item $D$ is the $\DyadicRatCoreUp$ scale row. It records the positive dyadic mesh, endpoint comparison cells, midpoint arithmetic cells, and halving bounds used by $B$.
\item $W$ is the $\StreamNameUp$ finite-window row for endpoint, midpoint, retained-child, and schedule-prefix observations.
\item $R$ is the $\RegSeqRatUp$ readback row obtained only after $I,B,D,W$ have been displayed.
\item $Q$ is the terminal $\RealUp$ seal row, opened only after the finite schedule and regular readback rows are exposed.
\item $H$ records componentwise $\hsame$ transport for the interval source, branch schedule, dyadic scale, stream windows, regular readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a located interval or Cauchy request through $I,B,D,W,R,Q,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DyadicBisectionScheduleUp$, $\ClosedIntervalBisectionUp$, $\LocatedIntervalBolzanoUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DyadicBisectionScheduleUp}$ row.
\end{enumerate}
The classifier compares accepted schedule carriers only through $I,B,D,W,R,Q,H,C,P,N$. It has no coordinate for an infinite choice sequence, a completed nested intersection, quotient real equality, host trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Dyadic bisection schedule NameCert obligations]
\label{thm:dyadic-bisection-schedule-namecert-obligations}
For every accepted $\DyadicBisectionScheduleUp$ carrier $S=(I,B,D,W,R,Q,H,C,P,N)$, the local $\NameCert_{\DyadicBisectionScheduleUp}$ surface consists exactly of carrier admission, closed-interval source exposure, finite branch-schedule exposure, dyadic halving exactness, stream-window exposure, regular rational readback, terminal real sealing, componentwise transport, displayed replay, package provenance, and local naming for the carrier of \autoref{def:dyadic-bisection-schedule-carrier}.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dyadic-bisection-schedule-carrier}. The interval row $I$ and branch row $B$ are the only rows that expose closed-interval bisection data, so every schedule obligation starts with the displayed finite interval source and retained-child ledger.

The dyadic and stream obligations are consecutive. The row $D$ supplies midpoint arithmetic, positive mesh data, and halving bounds before $W$ can open endpoint, midpoint, retained-child, or prefix observations.

The readback rows $R,Q$ are therefore downstream of $I,B,D,W$. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite route.

Since the carrier contains no coordinate for infinite branch choice, completed intersection points, quotient real equality, trichotomy, open-cover compactness, or ambient completeness, the listed obligations exhaust the local certificate.
\end{proof}

\begin{theorem}[Dyadic bisection schedule Cauchy handoff]
\label{thm:dyadic-bisection-schedule-cauchy-handoff}
Every Cauchy- or Bolzano-facing consumer of an accepted $\DyadicBisectionScheduleUp$ carrier reaches regular rational data only through the displayed route
$$
\ClosedIntervalBisectionUp
\longmapsto
\DyadicRatCoreUp
\longmapsto
\StreamNameUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The handoff may be consumed by located interval and completion routes as a finite halving schedule, but it exports no selected infinite branch, completed intersection point, quotient real representative, countable-choice schedule, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the accepted carrier $S=(I,B,D,W,R,Q,H,C,P,N)$. The source row $I$ and the retained branch schedule $B$ expose the only finite bisection information available to the consumer.

Read the dyadic row $D$ next. It fixes the midpoint and width-halving budget through displayed dyadic cells, so the schedule cannot be interpreted as an external sequence of arbitrary cuts.

The stream and regular rows $W,R$ then turn the displayed finite windows into regular rational readback. The terminal row $Q$ is a Real-facing seal only after this finite route has been read.

Finally $H,C,P,N$ preserve the same order under transport, replay, provenance, and local naming. Because no stronger object appears among the carrier coordinates, every Cauchy handoff remains the displayed finite schedule route.
\end{proof}

\falsifiablePrediction{A Cauchy or Bolzano consumer that omits the branch schedule row, dyadic halving row, StreamName window row, or RegSeqRat readback row cannot claim a $\DyadicBisectionScheduleUp$ handoff to a Real-facing seal.}

\independenceWitness{closed-interval-bisection, located-interval-bolzano, dyadicratcore, streamname, regseqrat, real: $\DyadicBisectionScheduleUp$ is not bijective to any listed sibling because it jointly carries an interval source, finite branch schedule, dyadic halving ledger, stream windows, regular readback, a terminal Real seal, transport, replay, provenance, and local naming.}

\closureat{DyadicBisectionScheduleUp}{seedStr}

\begin{closurestatus}{\DyadicBisectionScheduleUp}
  \constructivestory{A $\DyadicBisectionScheduleUp$ packet is generated from a closed-interval source row, a finite retained-branch schedule row, a DyadicRatCore halving ledger, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dyadic-bisection-schedule-carrier}, \autoref{thm:dyadic-bisection-schedule-namecert-obligations}, and \autoref{thm:dyadic-bisection-schedule-cauchy-handoff} seed the finite dyadic interval-halving route over ClosedIntervalBisectionUp, LocatedIntervalBolzanoUp, DyadicRatCoreUp, StreamNameUp, RegSeqRatUp, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected infinite branches, completed interval intersections, quotient real equality, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, interval-source exposure, finite branch-schedule exposure, dyadic halving exactness, StreamName window exactness, RegSeqRat readback, Real-seal nonescape, componentwise transport, displayed replay, package provenance, and local NameCert field faithfulness for BEDC.Derived.DyadicBisectionScheduleUp.}
\end{closurestatus}
