\chapter{A Concrete Naming Certificate for $\MetricCompletionLeftAdjointUp$}
\label{ch:concrete-instances-metric-completion-left-adjoint-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and Kelley on uniform and metric extension, the $\MetricCompletionLeftAdjointUp$ packet records the completion reflector as a left-adjoint NameCert boundary. It sits after the metric completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the dense embedding route of \autoref{ch:concrete-instances-metric-completion-dense-embedding-namecert}, the Cauchy completion adjunction surface of \autoref{ch:concrete-instances-cauchy-completion-adjunction-namecert}, the metric adjunction packet of \autoref{ch:concrete-instances-metric-completion-adjunction-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the reflector boundary without quotient representatives, host equality of completions, countable choice, selected limits, or ambient completeness.

\begin{definition}[MetricCompletionLeftAdjoint carrier]
\label{def:metric-completion-left-adjoint-carrier}
A $\MetricCompletionLeftAdjointUp$ carrier is a finite $\BHist$ packet
$$
L=(M,D,A,J,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricCompletionUp$ source reflector row.
\item $D$ is the $\MetricCompletionDenseEmbeddingUp$ unit row exposing the dense source inclusion.
\item $A$ is the $\CauchyCompletionAdjunctionUp$ adjunction row for completion-facing universal reads.
\item $J$ is the $\MetricCompletionAdjunctionUp$ metric adjunction row binding the same source, unit, counit, and triangle ledger.
\item $R$ is the $\RegSeqRatUp$ readback row opened by completion consumers.
\item $E$ is the terminal $\RealUp$ seal reached only after $M,D,A,J,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for reflector, dense embedding, adjunction, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a metric-source request through the reflector, dense unit, adjunction handoff, regular readback, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionLeftAdjointUp$, $\MetricCompletionUp$, $\MetricCompletionDenseEmbeddingUp$, $\CauchyCompletionAdjunctionUp$, $\MetricCompletionAdjunctionUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricCompletionLeftAdjointUp}$ row.
\end{enumerate}
The classifier accepts exactly packets with these ten displayed rows. It has no coordinate for quotient completion classes, chosen representatives, host equality of completion objects, countable-choice schedules, selected limits, or ambient complete metric spaces.
\end{definition}

\begin{theorem}[MetricCompletionLeftAdjoint NameCert obligations]
\label{thm:metric-completion-left-adjoint-namecert-obligations}
For every accepted $\MetricCompletionLeftAdjointUp$ carrier $L=(M,D,A,J,R,E,H,C,P,N)$, the local $\NameCert_{\MetricCompletionLeftAdjointUp}$ surface consists exactly of six finite obligations:
\begin{enumerate}
\item carrier admission for the displayed reflector, dense embedding, adjunction, regular readback, Real seal, transport, replay, provenance, and local naming rows;
\item unit exposure, requiring every source-to-completion read to pass through $D$ before the adjunction rows are consumed;
\item left-adjoint handoff, requiring $A$ and $J$ to name the same finite completion reflector route before any universal consumer reads it;
\item triangle and extension visibility, requiring the unit, counit, and triangle comparison inherited from the adjunction rows to remain displayed through $H$ and $C$;
\item RegSeqRat/Real seal nonescape, requiring $R$ and $E$ to be reached only after the reflector and adjunction rows have been displayed;
\item exhaustion of transport, replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:metric-completion-left-adjoint-carrier}. The tuple displays the full finite row inventory made available to the local certificate.

The source boundary is read through $M$ and $D$. The reflector row supplies the completion-facing carrier, while the dense embedding row is the displayed unit of the reflector.

The universal boundary is then read through $A$ and $J$. The Cauchy adjunction and metric adjunction rows provide the same finite source, unit, counit, and triangle ledger, so the left-adjoint handoff is a NameCert route rather than a host categorical equality.

Finally $R,E,H,C,P,N$ seal and replay the route for downstream consumers. Since quotient classes, selected representatives, choice schedules, host equality, and ambient completeness are absent from the carrier, the listed obligations exhaust the certificate surface.
\end{proof}

\begin{theorem}[MetricCompletionLeftAdjoint universal handoff]
\label{thm:metric-completion-left-adjoint-universal-handoff}
Every separated-completion, Real-facing, or universal-completion consumer of an accepted $\MetricCompletionLeftAdjointUp$ packet factors through the finite route
$$
\MetricCompletionUp
\longmapsto
\MetricCompletionDenseEmbeddingUp
\longmapsto
\CauchyCompletionAdjunctionUp
\longmapsto
\MetricCompletionAdjunctionUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The consumer receives source metric admission, dense unit exposure, adjunction handoff, triangle visibility, regular readback, Real sealing, componentwise transport, displayed replay, provenance, and local naming. It receives no quotient completion, selected representative, host equality of completions, countable choice, selected limit, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the accepted carrier $L=(M,D,A,J,R,E,H,C,P,N)$. A universal read opens $M$ first and then the dense unit row $D$, so the source-to-completion boundary is displayed before the adjunction rows are available.

Next consume $A$ and $J$. These rows expose the Cauchy and metric adjunction handoffs over the same finite reflector route, including the unit, counit, and triangle comparison needed by universal consumers.

The read then passes through $R$ and $E$. Regular rational readback and the terminal Real seal are downstream from the displayed reflector and adjunction rows, not independent completeness assumptions.

The structural rows $H,C,P,N$ preserve the ordered handoff under transport, replay, provenance, and local naming. Row exhaustion excludes quotient representatives, selected limits, host equality, countable choice, and ambient completeness from the exported certificate.
\end{proof}

\falsifiablePrediction{Every accepted $\MetricCompletionLeftAdjointUp$ universal read factors through MetricCompletion, MetricCompletionDenseEmbedding, CauchyCompletionAdjunction, MetricCompletionAdjunction, RegSeqRat, Real, transport, replay, provenance, and local naming rows.}

\independenceWitness{metriccompletion, metric-completion-dense-embedding, cauchy-completion-adjunction, metric-completion-adjunction, regseqrat, real: $\MetricCompletionLeftAdjointUp$ is not bijective to any listed sibling because it jointly packages reflector admission, dense unit exposure, adjunction handoff, triangle visibility, regular readback, Real sealing, transport, replay, provenance, and local naming.}

\closureat{MetricCompletionLeftAdjointUp}{seedStr}

\begin{closurestatus}{\MetricCompletionLeftAdjointUp}
  \constructivestory{A $\MetricCompletionLeftAdjointUp$ packet is generated from a MetricCompletion reflector row, a MetricCompletionDenseEmbedding unit row, CauchyCompletionAdjunction and MetricCompletionAdjunction handoff rows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-left-adjoint-carrier}, \autoref{thm:metric-completion-left-adjoint-namecert-obligations}, and \autoref{thm:metric-completion-left-adjoint-universal-handoff} seed the finite left-adjoint completion reflector route over metric completion, dense embedding, adjunction, regular readback, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completions, selected representatives, host equality of completions, countable choice, selected limits, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, unit exposure, left-adjoint handoff, triangle visibility, RegSeqRat/Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.MetricCompletionLeftAdjointUp.}
\end{closurestatus}
