\chapter{A Concrete Naming Certificate for $\BishopLocatedCompletenessUp$}
\label{ch:concrete-instances-bishop-located-completeness-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopLocatedCompletenessUp$ packet records the constructive completeness readback surface for located regular real names as finite BEDC NameCert data. It sits after the compact interval neighbor of \autoref{ch:concrete-instances-bishop-compact-interval-namecert}, the located interval surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite route by which a completion-facing consumer reads located Cauchy data; it does not assert ambient $\RealUp$ completeness, quotient equality of real names, countable choice, selected limits, or open-cover compactness.

\begin{definition}[Bishop located completeness carrier]
\label{def:bishop-located-completeness-carrier}
A $\BishopLocatedCompletenessUp$ carrier is a finite $\BHist$ packet
$$
L=(I,S,R,D,E,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\LocatedRealIntervalUp$ source row, naming the located interval or located enclosure in which the inspected Cauchy data is read.
\item $S$ is the $\StreamNameUp$ window row, exposing the finite stream observations available at the requested precision.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row extracted from those windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling mesh, modulus, and endpoint precision requests.
\item $E$ is the terminal $\RealUp$ seal row for the displayed readback route.
\item $B$ is the $\BishopCompactIntervalUp$ boundary row, recording that any compact-interval assistance is consumed only through the finite route of the Bishop compact interval packet.
\item $H$ records componentwise $\hsame$ transport for located interval, stream, regular, dyadic, Real, compact-boundary, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from located requests through stream windows, regular readback, dyadic tolerance, Real sealing, compact-boundary control, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\BishopLocatedCompletenessUp$, $\LocatedRealIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BishopCompactIntervalUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BishopLocatedCompletenessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,S,R,D,E,B,H,C,P,N$. It has no coordinate for host real completeness, quotient representatives, selected Cauchy limits, countable-choice schedules, open-cover compactness, or an unrestricted locator oracle.
\end{definition}

\begin{theorem}[Bishop located completeness NameCert obligations]
\label{thm:bishop-located-completeness-namecert-obligations}
For every accepted $\BishopLocatedCompletenessUp$ carrier $L=(I,S,R,D,E,B,H,C,P,N)$, the local $\NameCert_{\BishopLocatedCompletenessUp}$ surface consists exactly of carrier admission for the displayed located interval, stream-window, regular readback, dyadic tolerance, Real seal, compact-boundary, transport, replay, provenance, and naming rows; located source admission through $I$; finite observation through $S$; regular readback through $R$; dyadic tolerance accounting through $D$; Real sealing through $E$; compact-interval boundary control through $B$; componentwise transport through $H$; displayed replay through $C$; provenance through $P$; and local naming through $N$.

No obligation is discharged by ambient $\RealUp$ completeness, quotient equality of real names, a selected limit, countable choice, open-cover compactness, or a host locator outside the displayed packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-located-completeness-carrier}. The tuple lists the complete finite row inventory admitted by the local certificate.

The located source is read through $I$, then finite observation and regular readback pass through $S$ and $R$. Dyadic precision is controlled by $D$ before the Real seal $E$ is exposed.

The compact-interval row $B$ contributes only the finite boundary route supplied by \autoref{ch:concrete-instances-bishop-compact-interval-namecert}. It cannot be read as open-cover compactness or as ambient completeness.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed route. Since the carrier has no coordinate for quotient equality, selected limits, countable choice, or a host locator, no local $\NameCert_{\BishopLocatedCompletenessUp}$ obligation can export one.
\end{proof}

\begin{theorem}[Bishop located completeness Real-seal boundary]
\label{thm:bishop-located-completeness-real-seal-boundary}
Every completion-facing read from an accepted $\BishopLocatedCompletenessUp$ packet reaches $\RealUp$ only through the finite route
$$
\LocatedRealIntervalUp
\longmapsto
\StreamNameUp
\longmapsto
\RegSeqRatUp
\longmapsto
\DyadicRatCoreUp
\longmapsto
\BishopCompactIntervalUp
\longmapsto
\RealUp .
$$
The read exposes located interval data, finite stream windows, regular rational readback, dyadic tolerance control, compact-interval boundary control, Real sealing, transport, replay, provenance, and local naming, but it exports no ambient $\RealUp$ completeness theorem, quotient real equality, selected limit, countable-choice schedule, or open-cover compactness principle.
\end{theorem}
\begin{proof}
Let $L=(I,S,R,D,E,B,H,C,P,N)$ be an accepted carrier. A completion-facing consumer first receives $I,S,R,D$, so the located source, finite windows, regular readback, and dyadic tolerance route are fixed before any seal is visible.

The compact-boundary row $B$ is then read as the Bishop compact interval neighbor of \autoref{ch:concrete-instances-bishop-compact-interval-namecert}. It contributes only the finite interval boundary route accepted by that packet.

The Real-facing endpoint is $E$, and the structural route is $H,C,P,N$. These rows preserve the same finite path under transport, replay, provenance, and local naming. Because the classifier lacks coordinates for selected limits, quotient representatives, countable choice, open-cover compactness, and ambient completeness, the Real seal cannot be read as any of those stronger principles.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopLocatedCompletenessUp$ completion-facing read passes through LocatedRealIntervalUp, StreamNameUp, RegSeqRatUp, DyadicRatCoreUp, BishopCompactIntervalUp, RealUp, transport, replay, provenance, and local naming rows before any Real-facing output is visible.}

\independenceWitness{bishop-compact-interval, located-real-interval, streamname, regseqrat, dyadicratcore, real: $\BishopLocatedCompletenessUp$ is not bijective to any listed sibling because it jointly carries located source data, finite windows, regular rational readback, dyadic tolerance, compact-boundary control, terminal Real sealing, transport, replay, provenance, and local naming.}

\closureat{BishopLocatedCompletenessUp}{seedStr}

\begin{closurestatus}{\BishopLocatedCompletenessUp}
  \constructivestory{A $\BishopLocatedCompletenessUp$ packet is generated from a LocatedRealInterval source row, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a RealUp seal, a BishopCompactInterval boundary row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-located-completeness-carrier}, \autoref{thm:bishop-located-completeness-namecert-obligations}, and \autoref{thm:bishop-located-completeness-real-seal-boundary} seed the finite constructive located-completeness route over located interval, stream, regular, dyadic, compact-boundary, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim ambient RealUp completeness, quotient real equality, selected limits, countable choice, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located source admission, finite observation, regular readback, dyadic tolerance accounting, Real sealing, compact-boundary control, transport, replay, provenance, and local naming for BEDC.Derived.BishopLocatedCompletenessUp.}
\end{closurestatus}
