\chapter{A Concrete Naming Certificate for $\CauchyTailEstimateUp$}
\label{ch:concrete-instances-cauchy-tail-estimate-namecert}
\origin{human}

Following Bishop and Bridges' constructive analysis of Cauchy sequences and finite tail bounds, the $\CauchyTailEstimateUp$ packet records the displayed route by which a requested tail index and dyadic radius become a bounded regular-rational read before any $\RealUp$ seal is consumed. It sits after the tail-filter surface of \autoref{ch:concrete-instances-cauchy-sequence-tail-filter-namecert} and the fast criterion of \autoref{ch:concrete-instances-fast-cauchy-criterion-namecert}, and it reads its tolerance, regular readback, and endpoint seal through \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet is a finite certificate for Real and Completion consumers; it is not a quotient sequence, a selected limit, countable choice, host real equality, trichotomy, or ambient real completeness.

\begin{definition}[Cauchy tail estimate carrier]
\label{def:cauchy-tail-estimate-carrier}
A $\CauchyTailEstimateUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,D,R,E,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the tail-index row, naming the finite threshold after which the estimate may be inspected.
\item $D$ is the $\DyadicRatCoreUp$ radius row, naming the dyadic tolerance used by the tail-bound comparison.
\item $R$ is the $\RegSeqRatUp$ readback row reached from the displayed tail window and radius data.
\item $E$ is the $\RealUp$ seal row available only after $T,D,R$ have been replayed.
\item $B$ is the tail-bound ledger, recording the finite comparison witnesses that keep every accepted read beyond $T$ inside the radius named by $D$.
\item $H$ records componentwise $\hsame$ transport for $T,D,R,E,B$ and for the continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tail request through $T$, $D$, $B$, $R$, and then $E$.
\item $P$ is the $\Pkg$ provenance over $\CauchySequenceTailFilterUp$, $\FastCauchyCriterionUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyTailEstimateUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by transporting the displayed tail threshold, dyadic radius, regular readback, real seal, tail-bound ledger, continuation, provenance, and local naming rows to a common finite surface. It has no coordinate for quotient stream equality, selected representatives, countable choice, host real equality, trichotomy, open-cover compactness, or ambient completeness.
\end{definition}

\begin{theorem}[Cauchy tail estimate NameCert obligations]
\label{thm:cauchy-tail-estimate-namecert-obligations}
For every accepted $\CauchyTailEstimateUp$ carrier $Q=(T,D,R,E,B,H,C,P,N)$, the local $\NameCert_{\CauchyTailEstimateUp}$ surface consists exactly of five obligation rows:
\begin{enumerate}
\item carrier admission for the displayed tail index, dyadic radius, regular readback, real seal, tail-bound ledger, transport, continuation, provenance, and local name;
\item classifier transport to a common $\CauchySequenceTailFilterUp$, $\FastCauchyCriterionUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ finite surface;
\item stability of $T,D,R,E,B$ under the componentwise $\hsame$ rows recorded in $H$;
\item handoff exactness requiring every real-facing read to pass through $T,D,B,R,E$ in that order;
\item refusal rows excluding quotient streams, selected limits, countable choice, host real equality, trichotomy, open-cover compactness, and ambient completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-tail-estimate-carrier}. The projection exposes exactly the tail-index row, dyadic radius row, regular readback row, real seal row, tail-bound ledger, transport row, continuation row, provenance row, and local naming row.

Classifier transport is componentwise. The rows in $H$ move the mathematical coordinates $T,D,R,E,B$ and the administrative coordinates $C,P,N$ to the same finite comparison surface.

Handoff exactness is read from the displayed continuation row. A tail request first reaches the threshold row $T$, then the dyadic radius row $D$, then the ledger row $B$ that witnesses the tail-bound comparison, then the regular readback $R$, and only then the real seal $E$.

The refusal rows are exhausted by the carrier inventory. Since the packet has no coordinate for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, open-cover compactness, or completeness, no local NameCert obligation can export those data.
\end{proof}

\begin{theorem}[Cauchy tail estimate RegSeqRat handoff]
\label{thm:cauchy-tail-estimate-regseqrat-handoff}
For every accepted $\CauchyTailEstimateUp$ carrier $Q=(T,D,R,E,B,H,C,P,N)$, every $\RegSeqRatUp$ consumer of $R$ factors through the tail-index row $T$, the $\DyadicRatCoreUp$ radius row $D$, and the tail-bound ledger $B$ before it can expose the $\RealUp$ seal row $E$. The handoff route is therefore finite and does not identify Cauchy names by quotient equality, select a limit, invoke countable choice, or appeal to ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a regular-rational consumer of $R$. Carrier admission lists $R$ only as the readback row reached from the displayed tail threshold and dyadic radius.

Replay the continuation row $C$. Its route sends the request first to $T$, checks the requested radius through $D$, reads the comparison witnesses in $B$, and only then exposes the regular rational row $R$.

Transport through $H$ preserves this dependency order. The package row $P$ and local name $N$ record provenance and naming for the same finite packet; they do not add a second readback coordinate.

Thus every $\RegSeqRatUp$ handoff factors through $T,D,B$ before $R$ and reaches $E$ only after that route has been displayed. The carrier contains no coordinate from which a bypass route could obtain quotient equality, selected limits, choice, host real equality, or completeness.
\end{proof}

\closureat{CauchyTailEstimateUp}{seedStr}

\begin{closurestatus}{\CauchyTailEstimateUp}
  \constructivestory{A $\CauchyTailEstimateUp$ packet is generated from a finite tail-index row, a $\DyadicRatCoreUp$ radius row, a $\RegSeqRatUp$ readback, a $\RealUp$ seal row, a tail-bound ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-tail-estimate-carrier}, \autoref{thm:cauchy-tail-estimate-namecert-obligations}, and \autoref{thm:cauchy-tail-estimate-regseqrat-handoff} bind the finite tail-bound carrier, local NameCert obligations, and RegSeqRat handoff route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Real completeness, quotient streams, selected limits, countable choice, host real equality, trichotomy, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, stability, handoff exactness, refusal rows, and TasteGate nontriviality with field faithfulness for $T,D,R,E,B,H,C,P,N$.}
\end{closurestatus}
