\chapter{A Concrete Naming Certificate for $\RegularSequenceLocalizationUp$}
\label{ch:concrete-instances-regular-sequence-localization-namecert}
\origin{human}

Following Bishop and Bridges' regular Cauchy presentation of constructive reals and Kelley's finite-local analysis of neighborhoods, the $\RegularSequenceLocalizationUp$ packet records a bounded observation window around a displayed regular Cauchy name as first-class NameCert data. It reads finite stream observations through \autoref{ch:concrete-instances-streamname-namecert}, measures the local radius through \autoref{ch:concrete-instances-dyadicratcore-namecert}, replays regular rational evidence through \autoref{ch:concrete-instances-regseqrat-namecert}, and reaches the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet is local: it exposes the center, dyadic radius ledger, finite observation windows, rational readback, seal ordering, transport, replay, provenance, and local name before any Real or Completion consumer may use the localized estimate.

\begin{definition}[Regular-sequence localization carrier]
\label{def:regular-sequence-localization-carrier}
A $\RegularSequenceLocalizationUp$ carrier is a finite $\BHist$ packet
$$
L=(a,\rho,W,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $a$ is the finite localization center row, naming the regular Cauchy datum around which the local estimate is inspected.
\item $\rho$ is the $\DyadicRatCoreUp$ radius ledger, recording the dyadic scale, comparison cells, and slack rows used by the local window.
\item $W$ is the finite $\StreamNameUp$ observation-window row, naming exactly the stream positions read at the requested local precision.
\item $Q$ is the $\RegSeqRatUp$ readback row, converting the displayed center, radius ledger, and window observations into regular rational estimate data.
\item $R$ is the terminal $\RealUp$ seal row, available only after $a,\rho,W,Q$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the center, radius ledger, window observations, regular rational readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a local estimate request through $a$, $\rho$, $W$, $Q$, and then $R$.
\item $P$ is the $\Pkg$ provenance over $\RegularSequenceLocalizationUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RegularCauchyEntourageBasisUp$, $\RegularCauchyLimitUniquenessUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularSequenceLocalizationUp}$ row.
\end{enumerate}
The classifier compares accepted localization packets only through $a,\rho,W,Q,R,H,C,P,N$. It has no coordinate for quotient stream equality, a selected host limit, countable choice, trichotomy, ambient real completeness, or a global neighborhood system beyond the displayed finite window.
\end{definition}

\begin{theorem}[Regular-sequence localization NameCert obligations]
\label{thm:regular-sequence-localization-namecert-obligations}
For every accepted $\RegularSequenceLocalizationUp$ carrier $L=(a,\rho,W,Q,R,H,C,P,N)$, the local $\NameCert_{\RegularSequenceLocalizationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the localization center, dyadic radius ledger, finite stream observation windows, regular rational readback, terminal real seal, componentwise transport, replay, provenance, and local naming rows;
\item radius-ledger stability, requiring every local estimate to read $\rho$ through the displayed $\DyadicRatCoreUp$ scale and not through a host real order;
\item window-read stability, requiring every accepted observation to pass through the finite $\StreamNameUp$ row $W$ before $\RegSeqRatUp$ readback is available;
\item readback exactness, requiring the route $a,\rho,W \longmapsto Q \longmapsto R$ before any Real or Completion consumer treats the estimate as localized regular-sequence data;
\item transport and replay stability for the same $a,\rho,W,Q,R,P,N$ route under $\hsame$ transport and $\Cont$ replay.
\end{enumerate}
No localization NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-sequence-localization-carrier}. Its mathematical rows are exactly the center $a$, dyadic radius ledger $\rho$, finite window row $W$, regular rational readback $Q$, and real seal $R$.

The radius and window obligations are read before the rational handoff. The ledger $\rho$ supplies only dyadic comparison data, and $W$ supplies only the finite stream observations displayed by the packet.

The readback obligation is then forced through $Q$. Since $Q$ is the sole $\RegSeqRatUp$ coordinate, the packet cannot replace the local estimate by quotient stream equality, a selected limit, countable choice, trichotomy, or ambient completeness.

Finally the rows $H,C,P,N$ transport, replay, source, and name the same route. They do not add analytic coordinates, so the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Regular-sequence localization window stability]
\label{thm:regular-sequence-localization-window-stability}
Let $L=(a,\rho,W,Q,R,H,C,P,N)$ be an accepted $\RegularSequenceLocalizationUp$ carrier. If a Real or Completion consumer requests a localized regular-sequence estimate, then every accepted replay factors through the finite window route
$$
a,\rho,W \longmapsto Q \longmapsto R \longmapsto H,C,P,N .
$$
Consequently the displayed dyadic radius ledger and finite $\StreamNameUp$ observation window remain stable under $\hsame$ transport and $\Cont$ replay before the terminal $\RealUp$ seal is consumed.
\end{theorem}
\begin{proof}
Begin with a localized estimate request. The carrier offers the center row $a$, the dyadic radius ledger $\rho$, and the finite window row $W$ as the only rows available before regular rational readback.

Replay through $C$. The replay opens $a$, then reads the dyadic comparison cells in $\rho$, then inspects the finite observations named by $W$, and only then exposes the $\RegSeqRatUp$ readback row $Q$.

Transport through $H$ preserves this route componentwise. The real seal $R$ and the structural rows $P,N$ are downstream of the same displayed path, so no replay can consume $\RealUp$ data before the local window and radius ledger have been shown.
\end{proof}

\falsifiablePrediction{Every accepted $\RegularSequenceLocalizationUp$ read used by a Real or Completion consumer displays a finite center row, one $\DyadicRatCoreUp$ radius ledger, one finite $\StreamNameUp$ observation window, one $\RegSeqRatUp$ readback row, one terminal $\RealUp$ seal row, and one local structural NameCert route before the estimate is treated as localized regular-sequence data.}

\independenceWitness{streamname, dyadicratcore, regseqrat, real: $\RegularSequenceLocalizationUp$ is not bijective to any listed sibling because it binds a localization center, radius ledger, finite observation windows, regular rational readback, terminal real seal, transport, replay, provenance, and local NameCert row into one local estimate packet.}

\closureat{RegularSequenceLocalizationUp}{seedStr}

\begin{closurestatus}{\RegularSequenceLocalizationUp}
  \constructivestory{A $\RegularSequenceLocalizationUp$ packet is generated from a finite localization center, a $\DyadicRatCoreUp$ radius ledger, finite $\StreamNameUp$ observation windows, $\RegSeqRatUp$ readback, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-sequence-localization-carrier}, \autoref{thm:regular-sequence-localization-namecert-obligations}, and \autoref{thm:regular-sequence-localization-window-stability} seed the finite local regular-sequence estimate route over center, radius, window, readback, and Real seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global real completeness, quotient stream equality, selected limits, countable choice, trichotomy, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, radius-ledger stability, finite-window stability, RegSeqRat readback exactness, Real seal ordering, transport, replay, provenance, and local naming for BEDC.Derived.RegularSequenceLocalizationUp.}
\end{closurestatus}
