\chapter{A Concrete Naming Certificate for $\CompactLebesgueNumberUp$}
\label{ch:concrete-instances-compact-lebesgue-number-namecert}
\origin{human}

Following Lebesgue, Heine--Borel compactness, and Bishop--Bridges compact metric analysis, the $\CompactLebesgueNumberUp$ packet records the compact finite cover-radius ledger used by the compact uniform-continuity proof of \autoref{ch:visions-compact-uniform-continuity}. It refines the compact-metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the finite positive-radius ledger of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, and the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet is a finite NameCert surface for compact finite nets, located cover radii, lower-bound folds, and uniform-modulus handoff; it is not open-cover compactness, a selected subcover, or an external minimum principle.

\begin{definition}[Compact Lebesgue-number carrier]
\label{def:compact-lebesgue-number-carrier}
A $\CompactLebesgueNumberUp$ carrier is a finite $\BHist$ packet
$$
L=(K,B,C,R,F,U,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row. It exposes compact finite-net and metric inspection data through the compact-metric chapter.
\item $B$ is the finite $\mathsf{ProbeBundle}$ cover spine naming the compact cover candidates inspected by the packet.
\item $C$ is the center and coverage ledger. It records center histories, located-ball membership rows, and the finite cover witness for every compact-source history read by the packet.
\item $R$ is the positive cover-radius row, read through dyadic and rational-ball radius data attached to the bundled probes.
\item $F$ is the $\FiniteLebesgueNumberUp$ lower-radius row. It folds the finite radius ledger to a positive radius below every displayed cover radius.
\item $U$ is the $\UniformModulusUp$ consumer handoff row. It exports the lower-radius ledger only after $K,B,C,R,F$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the compact source, bundle spine, coverage ledger, radius rows, finite Lebesgue-number row, uniform-modulus handoff, replay, provenance, and local name.
\item $Q$ records displayed $\Cont$ replay of the route
$$
K,B,C,R \longmapsto F \longmapsto U .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactLebesgueNumberUp$, $\CompactMetricUp$, $\FiniteLebesgueNumberUp$, $\UniformModulusUp$, $\DyadicRatCoreUp$, $\RationalBallUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CompactLebesgueNumberUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,B,C,R,F,U,H,Q,P,N$. It has no coordinate for an arbitrary open cover, a selected finite subcover, host compactness, a host minimum, quotient real equality, countable choice, or a uniform modulus detached from the finite lower-radius row.
\end{definition}

\begin{theorem}[Compact Lebesgue-number NameCert obligations]
\label{thm:compact-lebesgue-number-namecert-obligations}
For every accepted $\CompactLebesgueNumberUp$ carrier
$$
L=(K,B,C,R,F,U,H,Q,P,N),
$$
the local $\NameCert_{\CompactLebesgueNumberUp}$ surface consists exactly of the following finite rows:
\begin{enumerate}
\item carrier admission for the ten displayed rows;
\item compact-metric source exposure, requiring every compact-source read to pass through $K$;
\item finite ProbeBundle coverage exactness, requiring $B$ and $C$ to bind every compact-source history to a named cover probe and located-ball row;
\item positive radius ledger exactness, requiring $R$ to attach displayed dyadic and rational-ball radii to the bundled probes;
\item finite Lebesgue-number fold compatibility, requiring $F$ to be a $\FiniteLebesgueNumberUp$ row below every displayed radius in $R$;
\item uniform-modulus handoff, requiring $U$ to consume only the lower-radius row and the compact source route already displayed;
\item componentwise transport, displayed replay, provenance, and local naming for the same route through $H,Q,P,N$.
\end{enumerate}
No compact Lebesgue-number obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $L=(K,B,C,R,F,U,H,Q,P,N)$. The compact source, bundle, coverage, radius, lower-fold, uniform handoff, and structural rows are precisely the displayed carrier coordinates.

The compact and coverage obligations come first. The row $K$ supplies the compact-metric source, while $B$ and $C$ expose only named probes, center histories, located-ball reads, and finite cover witnesses.

The radius obligations are finite. The row $R$ records the positive radii attached to bundled probes, and $F$ records the $\FiniteLebesgueNumberUp$ lower-radius ledger below those radii. No host minimum or selected open subcover is needed to read $F$.

Finally $U,H,Q,P,N$ hand the lower radius to uniform-modulus consumers and preserve, replay, source, and name the same route. Since the excluded objects do not occur as carrier coordinates, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Compact Lebesgue-number uniform-modulus handoff]
\label{thm:compact-lebesgue-number-uniform-modulus-handoff}
Every compact-uniform-continuity or $\UniformModulusUp$ consumer of an accepted $\CompactLebesgueNumberUp$ carrier receives the finite route
$$
\CompactMetricUp
\longmapsto
B,C,R
\longmapsto
\FiniteLebesgueNumberUp
\longmapsto
\UniformModulusUp
\longmapsto
H,Q,P,N .
$$
Thus the finite cover-radius ledger of \autoref{ch:visions-compact-uniform-continuity} is exposed as compact-metric source data, named cover probes, positive radius rows, a finite Lebesgue-number lower-bound fold, and a uniform-modulus handoff. It exports no arbitrary open cover, selected subcover, host compactness theorem, host minimum, countable-choice selector, quotient real equality, or detached uniform modulus.
\end{theorem}
\begin{proof}
Start from the compact-metric source $K$. It provides the finite compact inspection data, while $B$ and $C$ record the actual cover spine and located coverage rows consumed by the packet.

Read the radius ledger $R$ and the finite lower-bound row $F$. The lower-bound row is a $\FiniteLebesgueNumberUp$ packet tied to the displayed probe radii, so it is not a host minimum and not a selected subcover argument.

The handoff row $U$ sends exactly this lower-radius ledger to the $\UniformModulusUp$ consumer. The transport, replay, provenance, and naming rows $H,Q,P,N$ preserve the same path.

Because the carrier has no coordinate for an arbitrary open cover, selected subcover, host compactness theorem, host minimum, choice, quotient real equality, or detached modulus, every compact-uniform-continuity read factors through the displayed route.
\end{proof}

\falsifiablePrediction{An accepted $\CompactLebesgueNumberUp$ read is refuted if a compact-uniform-continuity consumer exports a UniformModulusUp row without displaying CompactMetric source data, a ProbeBundle cover spine, located coverage rows, positive radius rows, a FiniteLebesgueNumber lower-bound fold, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{compactmetric, finite-lebesgue-number, uniformmodulus: none alone is bijective with $\CompactLebesgueNumberUp$ because the packet jointly carries compact source data, finite cover probes, located coverage rows, positive radii, lower-bound fold, uniform-modulus handoff, transport, replay, provenance, and local NameCert.}

\closureat{CompactLebesgueNumberUp}{seedStr}

\begin{closurestatus}{\CompactLebesgueNumberUp}
  \constructivestory{A $\CompactLebesgueNumberUp$ packet is generated from CompactMetricUp source data, a finite ProbeBundle cover spine, located coverage rows, positive dyadic and rational-ball radius rows, a FiniteLebesgueNumberUp lower-bound fold, UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-lebesgue-number-carrier}, \autoref{thm:compact-lebesgue-number-namecert-obligations}, and \autoref{thm:compact-lebesgue-number-uniform-modulus-handoff} seed the compact finite Lebesgue-number packet from compact-metric cover data through finite lower-radius folds to UniformModulusUp handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close arbitrary open-cover compactness, selected subcovers, host compactness, host minima, quotient real equality, countable choice, detached uniform moduli, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked compact-source exposure, ProbeBundle coverage exactness, positive-radius ledger stability, FiniteLebesgueNumber fold compatibility, UniformModulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.CompactLebesgueNumberUp.}
\end{closurestatus}
