\chapter{A Concrete Naming Certificate for $\HyperbolicHarmonicBoundaryMeasureUp$}
\label{ch:concrete-instances-hyperbolic-harmonic-boundary-measure-namecert}
\origin{ai}

The $\HyperbolicHarmonicBoundaryMeasureUp$ packet realizes the boundary-weighting route of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits after the Poisson-kernel certificate of \autoref{ch:concrete-instances-hyperbolic-poisson-kernel-namecert}, the visual-metric certificate of \autoref{ch:concrete-instances-hyperbolic-visual-metric-namecert}, the Busemann-boundary certificate of \autoref{ch:concrete-instances-hyperbolic-busemann-boundary-namecert}, the hyperbolic-metric certificate of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the disk carrier of \autoref{ch:concrete-instances-unitdisk-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite harmonic boundary-measure read; it is not a host measure space, sigma-algebra completion, selected boundary representative, ambient probability theorem, global field instance, or quotient boundary construction.

\begin{definition}[Hyperbolic harmonic boundary measure carrier]
\label{def:hyperbolic-harmonic-boundary-measure-carrier}
A $\HyperbolicHarmonicBoundaryMeasureUp$ carrier is a finite $\BHist$ packet
$$
M=(D,B,V,K,R,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ disk-coordinate row naming the finite interior observation from which boundary weighting is read.
\item $B$ is the $\HyperbolicBusemannBoundaryUp$ row naming the boundary face and its Busemann-level comparison data.
\item $V$ is the $\HyperbolicVisualMetricUp$ row naming the visual boundary distance used by the weighting request.
\item $K$ is the $\HyperbolicPoissonKernelUp$ row, displaying the Poisson-kernel weight over the same disk, boundary, visual-metric, and hyperbolic-metric rows.
\item $R$ is the $\RealUp$ seal row for the displayed boundary weight.
\item $W$ is the harmonic boundary-measure ledger, recording the finite boundary-weight rows accepted by the Poisson kernel before any measure read is exported.
\item $H$ records componentwise $\hsame$ transport for $D,B,V,K,R,W$ and for the replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from disk-coordinate admission through Busemann-boundary admission, visual-metric readback, Poisson-kernel weighting, real sealing, and harmonic boundary-measure ledger exposure.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicHarmonicBoundaryMeasureUp$, $\HyperbolicPoissonKernelUp$, $\HyperbolicVisualMetricUp$, $\HyperbolicBusemannBoundaryUp$, $\HyperbolicMetricUp$, $\UnitDiskUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicHarmonicBoundaryMeasureUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $D,B,V,K,R,W,H,C,P,N$. It has no coordinate for a host measure space, completed sigma algebra, selected boundary representative, ambient probability theorem, global field instance, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Hyperbolic harmonic boundary measure NameCert obligations]
\label{thm:hyperbolic-harmonic-boundary-measure-namecert-obligations}
For every accepted $\HyperbolicHarmonicBoundaryMeasureUp$ carrier $M=(D,B,V,K,R,W,H,C,P,N)$, the local $\NameCert_{\HyperbolicHarmonicBoundaryMeasureUp}$ surface consists exactly of disk-coordinate admission, Busemann-boundary exposure, visual-metric readback, Poisson-kernel weighting, $\RealUp$ seal handoff, harmonic boundary-measure ledger exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-harmonic-boundary-measure-carrier}. The projection exposes the disk row, boundary row, visual-metric row, Poisson-kernel row, real seal, harmonic boundary-measure ledger, and the structural rows.

The geometric read is ordered by $D,B,V,K,R,W$. A boundary-measure consumer first sees the disk coordinate, then the Busemann boundary face, then the visual metric, and only then the Poisson-kernel weight and real seal used by the ledger.

The rows $H,C,P,N$ transport, replay, source, and name this finite route. Since the carrier contains no host measure space, completed sigma algebra, selected boundary representative, ambient probability theorem, global field instance, Lean verification, or bridge checking, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Hyperbolic harmonic boundary measure Poisson route]
\label{thm:hyperbolic-harmonic-boundary-measure-poisson-route}
Every accepted harmonic boundary-measure read of a $\HyperbolicHarmonicBoundaryMeasureUp$ packet factors through the finite route
$$
\UnitDiskUp
\longmapsto
\HyperbolicMetricUp
\longmapsto
\HyperbolicBusemannBoundaryUp
\longmapsto
\HyperbolicVisualMetricUp
\longmapsto
\HyperbolicPoissonKernelUp
\longmapsto
\RealUp .
$$
The exported boundary measure is the Poisson-kernel-weighted ledger $W$ over the same disk and boundary rows. It exports no completed host measure, sigma-algebra completion, selected boundary representative, ambient probability theorem, global field instance, or quotient boundary object.
\end{theorem}
\begin{proof}
Open the disk-coordinate row $D$ and the Busemann-boundary row $B$. These rows fix the finite interior and boundary observations before any weight is inspected.

Read the visual metric and Poisson kernel next. The row $V$ supplies the boundary-distance comparison, and $K$ supplies the Poisson-kernel weight over the same hyperbolic metric and boundary route.

The real seal $R$ and measure ledger $W$ then record the displayed harmonic boundary weight. The rows $H,C,P,N$ preserve the route under transport, replay it for consumers, record provenance, and attach the local name.

Thus every accepted measure read passes through the Poisson-kernel route. The carrier has no coordinate from which a host measure space, completed sigma algebra, selected boundary representative, ambient probability theorem, global field instance, or quotient boundary construction could be exported.
\end{proof}

\falsifiablePrediction{Every accepted $\HyperbolicHarmonicBoundaryMeasureUp$ read must pass through $\HyperbolicPoissonKernelUp$, $\HyperbolicVisualMetricUp$, $\HyperbolicBusemannBoundaryUp$, $\HyperbolicMetricUp$, $\UnitDiskUp$, and $\RealUp$ rows before it exports a boundary-weight ledger.}

\independenceWitness{Nearest siblings: hyperbolic-poisson-kernel, hyperbolic-visual-metric, hyperbolic-busemann-boundary, hyperbolic-metric, and unitdisk. The packet is not bijective to any one sibling because it jointly binds disk-coordinate rows, Busemann boundary rows, visual metric readback, Poisson-kernel weighting, RealUp sealing, harmonic boundary-measure ledger exposure, transport, replay, provenance, and local NameCert rows.}

\closureat{HyperbolicHarmonicBoundaryMeasureUp}{seedStr}

\begin{closurestatus}{\HyperbolicHarmonicBoundaryMeasureUp}
  \constructivestory{A $\HyperbolicHarmonicBoundaryMeasureUp$ packet is generated from UnitDisk disk-coordinate rows, HyperbolicMetric route data, HyperbolicBusemannBoundary rows, HyperbolicVisualMetric rows, HyperbolicPoissonKernel weights, a RealUp seal, a harmonic boundary-measure ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-harmonic-boundary-measure-carrier}, \autoref{thm:hyperbolic-harmonic-boundary-measure-namecert-obligations}, and \autoref{thm:hyperbolic-harmonic-boundary-measure-poisson-route} seed the finite harmonic boundary-measure route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host measure spaces, completed sigma algebras, selected boundary representatives, ambient probability theorems, global field instances, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, disk-coordinate exposure, Busemann-boundary exposure, visual-metric readback, Poisson-kernel weighting, RealUp seal handoff, ledger stability, transport, replay, provenance, and TasteGate Nontrivial and FieldFaithful instances for BEDC.Derived.HyperbolicHarmonicBoundaryMeasureUp.}
\end{closurestatus}
