\chapter{A Concrete Naming Certificate for $\GleasonCoverUp$}
\label{ch:concrete-instances-gleason-cover-namecert}
\origin{human}

Following Gleason and Kelley on projective covers of compact Hausdorff spaces, the $\GleasonCoverUp$ packet records finite projective-cover, clopen-lift, compactification, and provenance rows. It sits beside the compact-target seal of \autoref{ch:concrete-instances-stone-cech-compactification-namecert}, the lower-hit and upper-miss hyperspace route of \autoref{ch:concrete-instances-vietoris-topology-namecert}, the local separation and compact-neighbourhood rows of \autoref{ch:concrete-instances-locally-compact-hausdorff-namecert}, and the finite compact-metric witness surface of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet names the traditional projective-cover boundary through displayed BEDC data; it does not import choice-selected irreducible maps, host Boolean algebras, quotient compacta, open-cover compactness, or ambient compact Hausdorff equality.

\begin{definition}[Gleason cover carrier]
\label{def:gleason-cover-carrier}
A $\GleasonCoverUp$ carrier is a finite $\BHist$ packet
$$
G=(X,E,M,L,B,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the compact-Hausdorff source row, read through the displayed compact target seal, topology rows, and separation rows already available to compactification consumers.
\item $E$ is the extremally disconnected projective-cover row, recording that the cover source is inspected only through finite projective-extension requests.
\item $M$ is the cover-map row from $E$ to $X$, including the finite surjective-read and irreducibility-test windows exposed to downstream compact Hausdorff consumers.
\item $L$ is the clopen-lift row, recording finite clopen lift requests and their replay through the same cover map.
\item $B$ is the compactification comparison row, comparing the cover map with the $\StoneCechCompactificationUp$ probe and compact-target rows.
\item $V$ is the $\VietorisTopologyUp$ closed-set row, recording the finite lower-hit and upper-miss observations used when compact-subset consumers inspect the cover.
\item $H$ records componentwise $\hsame$ transport for the compact-Hausdorff source, projective-cover row, cover-map row, clopen-lift row, compactification comparison row, Vietoris closed-set row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from compact Hausdorff source reads through projective-cover, clopen-lift, compactification, and closed-set consumers.
\item $P$ is the $\Pkg$ provenance over $\GleasonCoverUp$, $\StoneCechCompactificationUp$, $\VietorisTopologyUp$, $\LocallyCompactHausdorffUp$, $\CompactMetricUp$, $\TopologyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\GleasonCoverUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $X,E,M,L,B,V,H,C,P,N$. It has no coordinate for arbitrary projective resolutions, selected ultrafilters, quotient equality of compacta, open-cover compactness, choice of clopen bases, or host compact Hausdorff spaces outside the displayed packet.
\end{definition}

\begin{theorem}[Gleason cover projective-cover handoff]
\label{thm:gleason-cover-projective-cover-handoff}
Every compact-Hausdorff consumer of an accepted $\GleasonCoverUp$ carrier reads the cover only through the finite route
$$
X,E,M,L,B,V \longmapsto H,C,P,N .
$$
The route exposes the compact-Hausdorff source, extremally disconnected projective-cover row, cover-map row, clopen-lift row, compactification comparison row, Vietoris closed-set row, componentwise transport, displayed replay, provenance, and local naming. It exports no open-cover selection, quotient compactum equality, selected ultrafilter, host Boolean algebra, arbitrary clopen basis, or ambient projective-cover theorem.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:gleason-cover-carrier}. The compact-Hausdorff source is the row $X$, the projective-cover information is carried by $E$ and $M$, and the clopen-lift and compactification comparisons are the rows $L$ and $B$.

Read closed-set observations through $V$. This is the finite $\VietorisTopologyUp$ side of the packet, so lower-hit and upper-miss consumers inspect only displayed closed-set windows rather than a host hyperspace or quotient compactum.

Finally replay through $H,C,P,N$. These rows transport, continue, source, and name the same carrier, so a compact-Hausdorff consumer has no coordinate from which to obtain open-cover selection, quotient equality, selected ultrafilters, host Boolean algebras, arbitrary clopen bases, or an ambient projective-cover theorem.
\end{proof}

\closureat{GleasonCoverUp}{seedStr}

\begin{closurestatus}{\GleasonCoverUp}
  \constructivestory{A $\GleasonCoverUp$ packet is generated from compact-Hausdorff source rows, extremally disconnected projective-cover rows, cover-map rows, clopen-lift rows, compactification comparisons, Vietoris closed-set rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:gleason-cover-carrier} and \autoref{thm:gleason-cover-projective-cover-handoff} seed the finite projective-cover handoff surface for compact-Hausdorff consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary projective resolutions, selected ultrafilters, quotient compactum equality, open-cover compactness, choice of clopen bases, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, projective-cover handoff, clopen-lift replay, compactification comparison, Vietoris closed-set compatibility, provenance, and local naming for BEDC.Derived.GleasonCoverUp.}
\end{closurestatus}
