\chapter{A Concrete Naming Certificate for $\CauchyCompletionAdjunctionTriangleUp$}
\label{ch:concrete-instances-cauchy-completion-adjunction-triangle-namecert}
\origin{human}

Following Bishop and Bridges on completion and Mac Lane on adjunction triangular identities, the $\CauchyCompletionAdjunctionTriangleUp$ packet records the L10 completion handoff that keeps the completion functor, the regular Cauchy adjunction, the universal property, and the idempotence boundary visible in one finite certificate. It sits beside \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}, \autoref{ch:concrete-instances-cauchy-regular-completion-adjunction-namecert}, \autoref{ch:concrete-instances-completion-idempotence-namecert}, \autoref{ch:concrete-instances-cauchy-completion-reflection-namecert}, and \autoref{ch:concrete-instances-metric-completion-idempotence-namecert}. The packet names a triangular completion route; it does not assert quotient completion equality, selected limits, host functor extensionality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[CauchyCompletionAdjunctionTriangle carrier]
\label{def:cauchy-completion-adjunction-triangle-carrier}
A $\CauchyCompletionAdjunctionTriangleUp$ carrier is a finite $\BHist$ packet
$$
T=(F,A,U,I,R,W,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyCompletionFunctorUp$ row naming the source-to-completion functorial surface.
\item $A$ is the $\CauchyRegularCompletionAdjunctionUp$ row naming the regular Cauchy adjunction boundary.
\item $U$ is the $\CompletionUniversalPropertyUp$ row that exposes the extension and uniqueness handoff.
\item $I$ is the completion idempotence row, read through the completion idempotence and metric completion idempotence chapters.
\item $R$ is the $\RegSeqRatUp$ row carrying regular rational completion readback.
\item $W$ is the $\StreamNameUp$ finite observation window for the regular Cauchy route.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by the displayed completion windows.
\item $E$ is the terminal $\RealUp$ seal reached only after $F,A,U,I,R,W,D$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the functor, adjunction, universal-property, idempotence, regular readback, window, dyadic ledger, Real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay for the triangular route from functor and adjunction rows to universal handoff, idempotence boundary, and Real-facing seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionAdjunctionTriangleUp$, $\CauchyCompletionFunctorUp$, $\CauchyRegularCompletionAdjunctionUp$, $\CompletionUniversalPropertyUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyCompletionAdjunctionTriangleUp}$ row.
\end{enumerate}
The classifier accepts only packets whose completion-facing read traverses the displayed rows $F,A,U,I,R,W,D,E,H,C,P,N$. It has no coordinate for quotient completions, selected limits, host equality of completed objects, unrestricted functor extensionality, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[CauchyCompletionAdjunctionTriangle NameCert obligations]
\label{thm:cauchy-completion-adjunction-triangle-namecert-obligations}
For every accepted $\CauchyCompletionAdjunctionTriangleUp$ carrier $T=(F,A,U,I,R,W,D,E,H,C,P,N)$, the local $\NameCert_{\CauchyCompletionAdjunctionTriangleUp}$ obligations are exactly carrier admission, functor-row visibility, regular adjunction visibility, universal-property handoff, idempotence-boundary retention, regular-rational and stream-window readback, dyadic tolerance compatibility, Real seal nonescape, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier row by row from \autoref{def:cauchy-completion-adjunction-triangle-carrier}. Carrier admission exposes precisely the twelve displayed rows, so every local obligation has one visible coordinate.

Read the completion triangle in order. The functor row $F$ and regular adjunction row $A$ are available before the universal-property row $U$, and the idempotence row $I$ is read as a boundary on reusing the same completion surface.

The Real-facing part is downstream. Rows $R,W,D$ provide regular rational readback, finite windowing, and dyadic tolerance data before the terminal seal $E$ is visible.

Finally, $H,C,P,N$ transport, replay, source, and name the same route. Since no carrier coordinate supplies quotient completion equality, selected limits, host functor extensionality, countable choice, or ambient completeness, the displayed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[CauchyCompletionAdjunctionTriangle universal handoff]
\label{thm:cauchy-completion-adjunction-triangle-universal-handoff}
Every accepted $\CauchyCompletionAdjunctionTriangleUp$ carrier hands a completion-facing consumer from the $\CauchyCompletionFunctorUp$ row and the $\CauchyRegularCompletionAdjunctionUp$ row to the $\CompletionUniversalPropertyUp$ row before any idempotence or Real-facing read is exported. The handoff is the finite route
$$
F,A \longmapsto U \longmapsto I,R,W,D,E,H,C,P,N
$$
and not a quotient completion, selected limit, host equality of extensions, or ambient completeness assertion.
\end{theorem}
\begin{proof}
Begin with the functor and adjunction rows in the carrier. They are separate coordinates, so a consumer cannot read the universal-property row as a detached host theorem.

Project $U$. It is the only row that records extension and uniqueness handoff for the displayed completion route, and it is read after $F$ and $A$ have fixed the source completion surface.

The idempotence and Real-facing rows are downstream of that handoff. Row $I$ records reuse of the same completion boundary, while $R,W,D,E$ provide the finite regular-rational, window, dyadic, and Real seal route.

Rows $H,C,P,N$ preserve the same finite path. Thus the universal handoff is exactly the displayed route and cannot become quotient completion equality, selected-limit data, host extension equality, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyCompletionAdjunctionTriangle idempotence boundary]
\label{thm:cauchy-completion-adjunction-triangle-idempotence-boundary}
For every accepted $\CauchyCompletionAdjunctionTriangleUp$ carrier, the idempotence read $I$ is a boundary on reusing the already displayed completion route $F,A,U,R,W,D,E,H,C,P,N$. It cannot identify completed objects by host equality, erase the universal-property row, select a limit representative, or assert ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Open the accepted packet and isolate $I$. The carrier definition places $I$ after the completion functor, regular adjunction, and universal-property rows, not as an independent completed-object equality.

Use the universal handoff theorem. It forces the route through $F,A,U$ before $I$ can be consumed by a completion-facing reader.

The remaining rows $R,W,D,E,H,C,P,N$ show what the idempotence boundary may preserve: regular rational readback, finite observation windows, dyadic tolerances, the Real seal, transport, replay, provenance, and local naming. No row contains host equality of completions, selected representatives, erased universal handoff data, or ambient completeness.
\end{proof}

\falsifiablePrediction{A completion consumer that exports a Cauchy-completion triangle without displaying the functor, regular adjunction, universal-property, idempotence, RegSeqRat, StreamName, DyadicRatCore, Real seal, transport, replay, provenance, and local naming rows is not reading a $\CauchyCompletionAdjunctionTriangleUp$ packet.}

\independenceWitness{cauchycompletionfunctor, cauchyregularcompletionadjunction, completionidempotence, cauchycompletionreflection, metriccompletionidempotence: $\CauchyCompletionAdjunctionTriangleUp$ is not bijective to any listed sibling because it jointly carries functor, adjunction, universal-property, idempotence, regular-rational, window, dyadic, Real seal, transport, replay, provenance, and local naming rows.}

\closureat{CauchyCompletionAdjunctionTriangleUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionAdjunctionTriangleUp}
  \constructivestory{A $\CauchyCompletionAdjunctionTriangleUp$ packet is generated from a CauchyCompletionFunctor row, a CauchyRegularCompletionAdjunction row, a CompletionUniversalProperty row, a completion idempotence row, RegSeqRat readback, StreamName windows, a DyadicRatCore tolerance ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-adjunction-triangle-carrier}, \autoref{thm:cauchy-completion-adjunction-triangle-namecert-obligations}, \autoref{thm:cauchy-completion-adjunction-triangle-universal-handoff}, and \autoref{thm:cauchy-completion-adjunction-triangle-idempotence-boundary} seed the finite triangular handoff for the L10 Cauchy completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected limits, host functor extensionality, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, universal-property handoff, idempotence boundary, RegSeqRat and StreamName readback, DyadicRatCore compatibility, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCompletionAdjunctionTriangleUp.}
\end{closurestatus}
