\chapter{A Concrete Naming Certificate for $\CauchyCriterionForSeriesUp$}
\label{ch:concrete-instances-cauchy-criterion-for-series-namecert}
\origin{human}

Following Cauchy and Knopp, the $\CauchyCriterionForSeriesUp$ packet records the constructive criterion that a real series converges exactly when its finite tails become arbitrarily small under displayed regular-rational windows. It sits after the series carrier of \autoref{ch:concrete-instances-realseries-namecert}, the Cauchy sequence algebra of \autoref{ch:concrete-instances-cauchy-sequence-algebra-namecert}, the stream-name window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite tail route for series convergence; it is not a host infinite sum, quotient stream equality, selected limit, trichotomy, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy criterion for series carrier]
\label{def:cauchy-criterion-for-series-carrier}
A $\CauchyCriterionForSeriesUp$ carrier is a finite $\BHist$ packet
$$
S=(A,L,W,D,R,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the $\RealSeriesUp$ source row, displaying the inspected series terms and partial-sum prefix.
\item $L$ is the $\CauchySequenceAlgebraUp$ row, naming the partial-sum algebra and its finite sum/difference operations.
\item $W$ is the $\StreamNameUp$ window row, recording the finite tail interval and every inspected partial-sum index.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row, naming the positive dyadic radius used by the tail comparison.
\item $R$ is the $\RegSeqRatUp$ readback row reached from the displayed tail window and dyadic tolerance.
\item $E$ is the $\RealUp$ seal row available only after the series, algebra, window, tolerance, and readback rows have been replayed.
\item $T$ is the tail-smallness ledger, recording the finite witnesses that all displayed tails beyond the named threshold are inside the tolerance in $D$.
\item $H$ records componentwise $\hsame$ transport for $A,L,W,D,R,E,T$ and for the continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a convergence request through the source series, partial-sum algebra, finite window, dyadic tolerance, regular rational readback, tail-smallness ledger, and real seal.
\item $P$ is the $\Pkg$ provenance over $\CauchyCriterionForSeriesUp$, $\RealSeriesUp$, $\CauchySequenceAlgebraUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCriterionForSeriesUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $A,L,W,D,R,E,T,H,C,P,N$. It has no coordinate for an infinite host sum, quotient equality of partial-sum streams, selected limit, countable-choice modulus, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Cauchy criterion for series NameCert obligations]
\label{thm:cauchy-criterion-for-series-namecert-obligations}
For every accepted $\CauchyCriterionForSeriesUp$ carrier $S=(A,L,W,D,R,E,T,H,C,P,N)$, the local $\NameCert_{\CauchyCriterionForSeriesUp}$ surface consists exactly of carrier admission, $\RealSeriesUp$ source exposure, $\CauchySequenceAlgebraUp$ partial-sum algebra exposure, $\StreamNameUp$ tail-window exposure, $\DyadicRatCoreUp$ tolerance exposure, $\RegSeqRatUp$ readback, $\RealUp$ seal handoff, tail-smallness ledger readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-criterion-for-series-carrier}. The tuple displays the real-series source, partial-sum algebra, finite windows, dyadic tolerance, regular rational readback, real seal, tail-smallness ledger, transport, continuation, provenance, and local name.

The analytic content is read through $A,L,W,D,R,E,T$. The series row supplies terms and partial sums; the algebra row supplies finite partial-sum differences; the window and tolerance rows state the inspected tail request; and the readback, seal, and ledger rows certify that the displayed tail is small.

The structural rows $H,C,P,N$ preserve and replay the same route. Since the carrier contains no coordinate for host infinite sums, quotient stream equality, selected limits, countable choice, trichotomy, ambient completeness, or bridge checking, the listed rows exhaust the local certificate.
\end{proof}

\begin{theorem}[Cauchy criterion for series tail route]
\label{thm:cauchy-criterion-for-series-tail-route}
Every accepted convergence read of a $\CauchyCriterionForSeriesUp$ packet factors through the finite tail route
$$
\RealSeriesUp
\longmapsto
\CauchySequenceAlgebraUp
\longmapsto
\StreamNameUp
\longmapsto
\DyadicRatCoreUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The exported criterion is the assertion that the partial-sum tail ledger $T$ can answer each displayed dyadic tolerance request after the source series, partial-sum algebra, finite window, regular readback, and real seal have been displayed. It exports no host infinite sum, quotient partial-sum stream, selected limit, countable-choice modulus, trichotomy, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the source series row $A$ and partial-sum algebra row $L$. These rows provide only finite term and partial-sum data, so a convergence consumer has not yet received a completed sum.

Next read the finite request rows $W$ and $D$. The stream-name row displays the inspected tail window, and the dyadic row names the tolerance for that window.

The regular rational readback $R$, real seal $E$, and tail-smallness ledger $T$ then certify the displayed tail comparison. The continuation row $C$ fixes this order, and $H,P,N$ transport, source, and name the same packet.

Because every consumer reaches the criterion through this route, any read that asks for quotient stream equality, selected limits, countable choice, trichotomy, or ambient real completeness has left the packet and is not part of the exported criterion.
\end{proof}

\falsifiablePrediction{Every accepted $\CauchyCriterionForSeriesUp$ convergence read must expose a $\RealSeriesUp$ source row, $\CauchySequenceAlgebraUp$ partial-sum algebra row, $\StreamNameUp$ tail window, $\DyadicRatCoreUp$ tolerance, $\RegSeqRatUp$ readback, $\RealUp$ seal, tail-smallness ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ before the criterion is available.}

\independenceWitness{Nearest siblings: realseries, cauchysequencealgebra, streamname, dyadicratcore, regseqrat, and real. The packet is not bijective to any one sibling because it jointly binds source series rows, partial-sum algebra, tail windows, dyadic tolerances, regular rational readback, real sealing, tail-smallness ledger, transport, replay, provenance, and local NameCert rows.}

\closureat{CauchyCriterionForSeriesUp}{seedStr}

\begin{closurestatus}{\CauchyCriterionForSeriesUp}
  \constructivestory{A $\CauchyCriterionForSeriesUp$ packet is generated from a RealSeries source row, CauchySequenceAlgebra partial-sum row, StreamName tail-window row, DyadicRatCore tolerance row, RegSeqRat readback, RealUp seal, tail-smallness ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-criterion-for-series-carrier}, \autoref{thm:cauchy-criterion-for-series-namecert-obligations}, and \autoref{thm:cauchy-criterion-for-series-tail-route} seed the finite constructive Cauchy criterion route for real series.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host infinite sums, quotient stream equality, selected limits, countable choice, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source exposure, partial-sum algebra exposure, tail-window exactness, dyadic tolerance exactness, RegSeqRat readback, RealUp seal handoff, tail-smallness ledger stability, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCriterionForSeriesUp.}
\end{closurestatus}
