\chapter{A Concrete Naming Certificate for $\ProductUniformSpaceUp$}
\label{ch:concrete-instances-product-uniform-space-namecert}
\origin{human}

Following Bourbaki and Weil's product uniformity language, the $\ProductUniformSpaceUp$ packet records the finite route by which two displayed uniform source packets are assembled into a product uniformity without importing a host product topology. It reads the $\UniformSpaceUp$ entourage surface of \autoref{ch:concrete-instances-uniformspace-namecert}, the $\ProductUp$ projection route of \autoref{ch:concrete-instances-prod-namecert}, the metric-compatible source of \autoref{ch:concrete-instances-metric-namecert}, and the completion-facing boundary of \autoref{ch:concrete-instances-completion-namecert}. The chapter names the product-entourage rows needed by completion consumers before any quotient completion, unrestricted entourage choice, or ambient topology is visible.

\begin{definition}[Product uniform space carrier]
\label{def:product-uniform-space-carrier}
A $\ProductUniformSpaceUp$ carrier is a finite $\BHist$ packet
$$
U=(A,B,\Pi,E_A,E_B,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two uniform source packets. Each source exposes only its displayed carrier, entourage ledger, diagonal row, symmetry row, composition-refinement row, transport row, replay row, provenance row, and local $\NameCert$ row.
\item $\Pi$ is the $\ProductUp$ projection row. It records the left and right projection reads and the paired point-name admission used by the product packet.
\item $E_A$ and $E_B$ are the paired entourage ledgers. A product entourage request must name a left source entourage from $A$ and a right source entourage from $B$ before it can be read as a product request.
\item $W$ is the finite componentwise witness row. It records that a product pair is accepted exactly by its two projected source reads and their paired entourage ledgers.
\item $H$ records componentwise $\hsame$ transport for the two source packets, the projection row, the paired entourage ledgers, the witness row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a product-entourage request through the projection row, the left and right source entourages, the componentwise witness, transport, provenance, and local naming rows.
\item $P$ is the $\Pkg$ provenance over $\ProductUniformSpaceUp$, $\UniformSpaceUp$, $\ProductUp$, $\MetricSpaceUp$, $\CompletionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ProductUniformSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $A,B,\Pi,E_A,E_B,W,H,C,P,N$. It has no coordinate for host product topology, unrestricted choice of entourages, quotient completion, selected limits, open-cover compactness, or bridge checking.
\end{definition}

\begin{theorem}[Product uniform space NameCert obligations]
\label{thm:product-uniform-space-namecert-obligations}
For every accepted $\ProductUniformSpaceUp$ carrier $U=(A,B,\Pi,E_A,E_B,W,H,C,P,N)$, the local $\NameCert_{\ProductUniformSpaceUp}$ surface consists exactly of carrier admission for the two $\UniformSpaceUp$ source packets, the $\ProductUp$ projection row, the paired left and right entourage ledgers, the finite componentwise witness row, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. No product-uniformity obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:product-uniform-space-carrier}. The tuple displays exactly the two source packets, projection row, paired entourage ledgers, witness row, transport, replay, provenance, and local naming.

The source rows provide the only uniform data available to the packet. A product-entourage read must therefore pass through $A$ and $B$ and then through the named ledgers $E_A$ and $E_B$.

The projection row $\Pi$ and witness row $W$ bind the product read to the two component reads. Transport by $H$ is componentwise, and replay by $C$ follows the same displayed route.

Since $P$ and $N$ only source and name this finite surface, and since no other carrier coordinate remains, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Product uniform space projection-entourage route]
\label{thm:product-uniform-space-projection-entourage-route}
Every completion-facing or metric-compatible read of an accepted $\ProductUniformSpaceUp$ carrier factors through the finite route
$$
\ProductUp \longmapsto (\UniformSpaceUp,\UniformSpaceUp) \longmapsto \CompletionUp .
$$
More explicitly, a consumer first reads the projection row $\Pi$, then the left and right uniform source packets $A,B$, then the paired entourage ledgers $E_A,E_B$, and only afterward the witness, transport, replay, provenance, and local naming rows $W,H,C,P,N$. The route exports no host product topology, unrestricted entourage selector, quotient completion, selected limit, or ambient bridge proof.
\end{theorem}
\begin{proof}
Start with the accepted carrier and the obligations of \autoref{thm:product-uniform-space-namecert-obligations}. The product request is not available before $\Pi$ displays the two projections and paired point-name admission.

Each projected read then enters one source uniform packet. The left and right entourage data are the displayed ledgers $E_A$ and $E_B$, so the product entourage is a finite pair of component ledgers rather than a host-level neighbourhood of a product topology.

The completion-facing part reads only the same finite route. The witness row $W$ records componentwise acceptance, while $H,C,P,N$ transport, replay, source, and name that route for $\MetricSpaceUp$ and $\CompletionUp$ consumers.

Because the carrier has no coordinate for host product topology, unrestricted entourage choice, quotient completion, selected limits, or bridge checking, no consumer can project those objects from the packet.
\end{proof}

\closureat{ProductUniformSpaceUp}{seedStr}

\begin{closurestatus}{\ProductUniformSpaceUp}
  \constructivestory{A $\ProductUniformSpaceUp$ packet is generated from two UniformSpace source packets, a Product projection row, paired component entourage ledgers, a finite componentwise witness row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:product-uniform-space-carrier}, \autoref{thm:product-uniform-space-namecert-obligations}, and \autoref{thm:product-uniform-space-projection-entourage-route} seed the finite product-uniformity route used by metric-compatible completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host product topology, unrestricted choice of entourages, quotient completion, selected limits, Lean verification, or bridge checking for $\ProductUniformSpaceUp$.}
  \upgradepath{Obligation closure requires checked source carrier admission, projection coverage, paired entourage exactness, componentwise transport, replay stability, provenance, local naming, and completion-route non-escape for BEDC.Derived.ProductUniformSpaceUp.}
\end{closurestatus}
