\chapter{A Concrete Naming Certificate for $\ArchimedeanCauchyCompleteFieldUp$}
\label{ch:concrete-instances-archimedean-cauchy-complete-field-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\ArchimedeanCauchyCompleteFieldUp$ packet records the Real-facing interface of an Archimedean Cauchy-complete ordered field as finite BEDC NameCert data. It reads the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational sequence readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic precision ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the algebraic order interface of \autoref{ch:concrete-instances-real-alg-order-namecert}, the Cauchy-complete ordered-field route of \autoref{ch:concrete-instances-cauchy-complete-ordered-field-namecert}, and the comparison capstone of \autoref{ch:concrete-instances-complete-archimedean-field-namecert}. The chapter provides one L10 phase-exit surface for Real and Completion consumers without importing a host complete ordered field.

\begin{definition}[Archimedean Cauchy-complete field carrier]
\label{def:archimedean-cauchy-complete-field-carrier}
An $\ArchimedeanCauchyCompleteFieldUp$ carrier is a finite $\BHist$ packet
$$
A=(R,Q,D,S,O,K,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ scalar seal, read only as the terminal Real name row.
\item $Q$ is the $\RegSeqRatUp$ readback row for regular rational names.
\item $D$ is the $\DyadicRatCoreUp$ precision ledger for displayed tolerance and radius requests.
\item $S$ is the finite $\StreamNameUp$ window through which rational observations are requested.
\item $O$ is the $\RealAlgOrderUp$ operation-and-order row, naming addition, multiplication, zero, one, positivity, and order comparison only as finite ledger entries.
\item $K$ is the $\CauchyCompleteOrderedFieldUp$ route row tying the Real seal, regular readback, dyadic ledger, stream window, and algebraic-order row to displayed Cauchy-complete ordered-field service.
\item $F$ is the $\CompleteArchimedeanFieldUp$ comparison row, recording the Archimedean comparison surface reached from the same displayed Cauchy-complete ordered-field route.
\item $H$ records componentwise $\hsame$ transport for the Real seal, regular readback, dyadic ledger, stream window, algebra-order row, Cauchy-complete ordered-field route, Archimedean comparison row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite precision request through stream observation, regular rational readback, Real sealing, order operation, Cauchy-complete route, Archimedean comparison, and local naming.
\item $P$ is the $\Pkg$ provenance over $\ArchimedeanCauchyCompleteFieldUp$, $\RealUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RealAlgOrderUp$, $\CauchyCompleteOrderedFieldUp$, $\CompleteArchimedeanFieldUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ArchimedeanCauchyCompleteFieldUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,Q,D,S,O,K,F,H,C,P,N$. It has no coordinate for quotient Real equality, trichotomy, selected limits, host supremum data, or ambient completeness.
\end{definition}

\begin{theorem}[Archimedean Cauchy-complete field NameCert obligations]
\label{thm:archimedean-cauchy-complete-field-namecert-obligations}
For every accepted $\ArchimedeanCauchyCompleteFieldUp$ carrier
$$
A=(R,Q,D,S,O,K,F,H,C,P,N),
$$
the local $\NameCert_{\ArchimedeanCauchyCompleteFieldUp}$ surface consists exactly of carrier admission for the Real scalar seal $R$, regular rational readback $Q$, dyadic precision ledger $D$, finite stream window $S$, RealAlgOrder operation-and-order row $O$, CauchyCompleteOrderedField route row $K$, CompleteArchimedeanField comparison row $F$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:archimedean-cauchy-complete-field-carrier}. The accepted tuple exposes exactly the Real seal, regular readback, dyadic ledger, finite stream window, algebra-order row, Cauchy-complete ordered-field route, Archimedean comparison row, transport, replay, provenance, and local naming rows.

The scalar and completion-facing part is read through $R,Q,D,S,K$. The row $K$ is allowed to cite the Cauchy-complete ordered-field surface only after the Real seal, regular readback, dyadic precision, and stream-window rows have been displayed.

The order and Archimedean comparison part is read through $O$ and $F$. These rows record operation, order, and comparison service as BEDC packet rows rather than as a host complete ordered-field structure.

Finally $H,C,P,N$ transport, replay, source, and name that finite surface. Since no other carrier coordinate remains, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Archimedean Cauchy-complete field L10 exit route]
\label{thm:archimedean-cauchy-complete-field-l10-exit-route}
Every L10 Real or Completion consumer of an accepted $\ArchimedeanCauchyCompleteFieldUp$ packet must factor its read through
$$
\RealUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \StreamNameUp,\ \RealAlgOrderUp,\ \CauchyCompleteOrderedFieldUp,\ \CompleteArchimedeanFieldUp
$$
as the displayed rows $R,Q,D,S,O,K,F,H,C,P,N$. Thus the packet supplies a single Archimedean Cauchy-complete ordered-field interface for Real-facing phase exit, but it exports no quotient Real equality, trichotomy, selected limit, host complete ordered field, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with an accepted consumer read. The Real scalar is exposed only by $R$, and the rational Cauchy evidence behind the read must pass through $Q,D,S$ before any completion-facing row is visible.

The algebraic and order part is then confined to $O$. Addition, multiplication, zero, one, positivity, and comparison are read as displayed operation-and-order rows, not as host-field operations.

The completion route is $K$, and the Archimedean comparison capstone is $F$. These rows link the same Real seal, regular readback, dyadic ledger, stream window, and order row to the Cauchy-complete ordered-field and CompleteArchimedeanField packets.

The structural rows $H,C,P,N$ preserve and name this route. Because the carrier lacks quotient Real equality, trichotomy, selected limit, host-field, and ambient-completeness coordinates, every L10 phase-exit read is confined to the finite surface stated above.
\end{proof}

\closureat{ArchimedeanCauchyCompleteFieldUp}{seedStr}

\begin{closurestatus}{\ArchimedeanCauchyCompleteFieldUp}
  \constructivestory{An $\ArchimedeanCauchyCompleteFieldUp$ packet is generated from a Real scalar seal, RegSeqRat readback, DyadicRatCore precision ledger, StreamName finite window, RealAlgOrder operation and order row, CauchyCompleteOrderedField route row, CompleteArchimedeanField comparison row, componentwise transport, displayed replay, package provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:archimedean-cauchy-complete-field-carrier}, \autoref{thm:archimedean-cauchy-complete-field-namecert-obligations}, and \autoref{thm:archimedean-cauchy-complete-field-l10-exit-route} seed the L10 Real and Completion phase-exit surface for Archimedean Cauchy-complete ordered-field consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient Real equality, trichotomy, selected limits, host complete ordered fields, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, rowwise operation and order service, Archimedean comparison service, transport, replay, provenance, and local naming for the same finite packet.}
\end{closurestatus}
