\chapter{A Concrete Naming Certificate for $\CompleteTotallyBoundedCompactMetricUp$}
\label{ch:concrete-instances-complete-totally-bounded-compact-metric-namecert}
\origin{human}

Following Bishop and Bridges and Kelley, the $\CompleteTotallyBoundedCompactMetricUp$ packet records the constructive compact-metric characterization in which complete metric service and total-bounded finite nets are carried as one public NameCert surface. It sits over the metric source of \autoref{ch:concrete-instances-metric-namecert}, the complete-metric service of \autoref{ch:concrete-instances-completemetric-namecert}, the finite-net surface of \autoref{ch:concrete-instances-totallybounded-namecert}, and the compact-metric interface of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet is a finite L10 route for regular Cauchy reads, finite $\mathsf{ProbeBundle}$ nets, compact-metric public export, $\StreamNameUp$ windows, and $\RegSeqRatUp$ readback; it is not an open-cover compactness theorem, selected subcover, hidden dense sequence, quotient completion equality, or ambient $\RealUp$ completeness principle.

\begin{definition}[Complete totally bounded compact-metric carrier]
\label{def:complete-totally-bounded-compact-metric-carrier}
A $\CompleteTotallyBoundedCompactMetricUp$ carrier is a finite $\BHist$ packet
$$
K=(M,C,T,Q,S,R,H,A,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ source row, including the carrier classifier, distance requests, ball comparisons, and finite observation histories consumed by the rest of the packet.
\item $C$ is the $\CompleteMetricUp$ service row for regular Cauchy point names over $M$. It exposes only displayed limit rows, convergence-distance ledgers, and completion-facing handoff data.
\item $T$ is the $\TotallyBoundedUp$ finite-net row. It records, for each displayed positive tolerance, a closed $\mathsf{ProbeBundle}$ of centers, membership rows, coverage-distance rows, and rational comparison ledgers.
\item $Q$ is the $\CompactMetricUp$ public row obtained by reading $C$ and $T$ over the same metric source $M$.
\item $S$ is the $\StreamNameUp$ finite-window row through which Cauchy names, center names, and compact-metric inspection requests are observed.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational tolerances used by $C$, $T$, and $Q$.
\item $H$ records componentwise $\hsame$ transport for the metric source, complete row, totally-bounded row, compact-metric row, stream windows, regular-rational readbacks, replay, provenance, and local name.
\item $A$ records displayed $\Cont$ replay of the route
$$
M,C,T,S,R \longmapsto Q .
$$
\item $P$ is the $\Pkg$ provenance over $\CompleteTotallyBoundedCompactMetricUp$, $\MetricSpaceUp$, $\CompleteMetricUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CompleteTotallyBoundedCompactMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,C,T,Q,S,R,H,A,P,N$. It has no coordinate for arbitrary open covers, selected finite subcovers, selected dense sequences, host quotient equality of Cauchy names, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Complete totally bounded compact-metric NameCert obligations]
\label{thm:complete-totally-bounded-compact-metric-namecert-obligations}
For every accepted $\CompleteTotallyBoundedCompactMetricUp$ carrier
$$
K=(M,C,T,Q,S,R,H,A,P,N),
$$
the local $\NameCert_{\CompleteTotallyBoundedCompactMetricUp}$ surface consists exactly of the following finite rows:
\begin{enumerate}
\item carrier admission for the ten displayed rows;
\item metric-source admission through $M$, requiring every distance and ball read to stay inside the named metric carrier;
\item complete-service admission through $C$, requiring every regular Cauchy read to expose its displayed limit and convergence ledger before any compact-metric consumer may use it;
\item total-bounded finite-net admission through $T$, requiring every tolerance request to expose its $\mathsf{ProbeBundle}$ centers, membership constructors, coverage rows, and rational comparison ledger;
\item compact-metric synthesis through $Q$, requiring the complete and total-bounded rows to be read over the same metric source;
\item $\StreamNameUp$ and $\RegSeqRatUp$ readback through $S$ and $R$ for all finite observation and tolerance windows;
\item componentwise transport, displayed replay, provenance, and local naming through $H,A,P,N$.
\end{enumerate}
No complete-totally-bounded compact-metric obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $K=(M,C,T,Q,S,R,H,A,P,N)$. The metric source, complete service, total-bounded finite nets, compact-metric export, observation windows, rational readbacks, and structural rows are exactly the displayed carrier coordinates.

The complete side is read through $C$ over the metric source $M$. Thus a Cauchy-name consumer sees only the displayed limit row, convergence-distance ledger, and the $\StreamNameUp$ and $\RegSeqRatUp$ windows carried by $S$ and $R$.

The total-bounded side is read through $T$. A tolerance request obtains only the finite $\mathsf{ProbeBundle}$ centers, membership rows, coverage distances, and rational comparison ledger already displayed in the carrier.

The compact-metric row $Q$ can be consumed only after both $C$ and $T$ have been read over the same $M$. The rows $H,A,P,N$ transport, replay, source, and name that same route.

Since arbitrary open covers, selected subcovers, selected dense sequences, quotient completion equality, countable choice, and ambient $\RealUp$ completeness do not occur as carrier coordinates, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Complete totally bounded compact-metric uniform handoff]
\label{thm:complete-totally-bounded-compact-metric-uniform-handoff}
Every compactness, completion, or compact-uniform consumer of an accepted $\CompleteTotallyBoundedCompactMetricUp$ carrier receives the finite route
$$
\MetricSpaceUp
\longmapsto
\CompleteMetricUp,\TotallyBoundedUp
\longmapsto
\StreamNameUp,\RegSeqRatUp
\longmapsto
\CompactMetricUp
\longmapsto
\BHist,\hsame,\Cont,\Pkg,\NameCert .
$$
Thus the L10 compact-metric characterization is exposed as a single finite BEDC packet: complete Cauchy service, total-bounded finite nets, shared metric-source exactness, finite stream windows, regular-rational tolerance readback, compact-metric public export, transport, replay, provenance, and local naming. It exports no arbitrary open cover, selected subcover, selected dense sequence, quotient Cauchy-name equality, countable-choice schedule, host compactness theorem, or ambient real-completeness row.
\end{theorem}
\begin{proof}
Start with the metric source $M$. It fixes the carrier classifier, distance requests, ball comparisons, and finite observation histories consumed by every later row.

Read the complete and total-bounded rows separately. The row $C$ supplies the displayed complete-metric limit service for regular Cauchy names, while $T$ supplies the finite $\mathsf{ProbeBundle}$ net service for positive tolerance requests.

The windows $S$ and $R$ make the route finite. They bind the stream observations and regular rational tolerances used by both the Cauchy side and the finite-net side.

Finally the compact-metric row $Q$ is read through the same metric source and the same $C,T,S,R$ route, while $H,A,P,N$ preserve, replay, source, and name the public export. The excluded objects have no carrier coordinate, so every downstream read factors through the displayed route.
\end{proof}

\falsifiablePrediction{Every accepted $\CompleteTotallyBoundedCompactMetricUp$ compact-metric read must display the complete-metric service row, the totally-bounded finite-net row, StreamName windows, RegSeqRat readbacks, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert before any CompactMetricUp export is public.}

\independenceWitness{metric, complete-metric, totallybounded, compactmetric: $\CompleteTotallyBoundedCompactMetricUp$ is not bijective to any listed sibling because it jointly carries metric-source exactness, complete Cauchy service, total-bounded finite nets, compact-metric export, finite stream windows, regular-rational tolerances, transport, replay, provenance, and local naming as one packet.}

\closureat{CompleteTotallyBoundedCompactMetricUp}{seedStr}

\begin{closurestatus}{\CompleteTotallyBoundedCompactMetricUp}
  \constructivestory{A $\CompleteTotallyBoundedCompactMetricUp$ packet is generated from a MetricSpaceUp source row, a CompleteMetricUp service row, a TotallyBoundedUp finite-net row, a CompactMetricUp export row, StreamNameUp windows, RegSeqRatUp readbacks, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:complete-totally-bounded-compact-metric-carrier}, \autoref{thm:complete-totally-bounded-compact-metric-namecert-obligations}, and \autoref{thm:complete-totally-bounded-compact-metric-uniform-handoff} seed the compact-metric characterization route over $\MetricSpaceUp$, $\CompleteMetricUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, arbitrary open-cover compactness, selected subcovers, selected dense sequences, quotient Cauchy-name equality, countable choice, host compactness, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, complete-service admission, total-bounded finite-net admission, compact-metric synthesis, StreamName and RegSeqRat readback, transport, replay, provenance, and local NameCert exactness for BEDC.Derived.CompleteTotallyBoundedCompactMetricUp.}
\end{closurestatus}
