\chapter{A Concrete Naming Certificate for $\BaireGenericResidualUp$}
\label{ch:concrete-instances-baire-generic-residual-namecert}
\origin{human}

Following Baire, Oxtoby, and Bishop--Bridges, the $\BaireGenericResidualUp$ packet records the constructive residual-point route through dense-open schedules rather than through a host countable intersection object. It sits over the Baire prefix of \autoref{ch:concrete-instances-bairespace-namecert}, the dense-open certificate surface of \autoref{ch:concrete-instances-bairecategory-namecert}, the complete-metric handoff of \autoref{ch:concrete-instances-completemetric-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter packages the residual thread consumed by later L10 complete-metric routes without adding countable choice, an external intersection point, quotient stream equality, or ambient real completeness.

\begin{definition}[Baire generic residual carrier]
\label{def:baire-generic-residual-carrier}
A $\BaireGenericResidualUp$ carrier is a finite $\BHist$ packet
$$
G=(B,D,M,S,W,R,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BaireSpaceUp$ prefix row naming the inspected basic-open source and its finite prefix probes.
\item $D$ is the dense-open schedule row inherited from the $\BaireCategoryUp$ packet, including the displayed finite list of dense requests currently consumed by the residual route.
\item $M$ is the $\CompleteMetricUp$ handoff row through which the nested ball thread is interpreted.
\item $S$ is the $\StreamNameUp$ window schedule selecting the finite prefix, dense-open, and completion observations visible at this stage.
\item $W$ is the stream-window ledger recording the inspected predecessor balls, successor balls, radius budgets, and finite membership checks.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational centers, radius comparisons, and tolerance data used by the thread.
\item $E$ is the terminal $\RealUp$ seal row reached only after the $B,D,M,S,W,R$ route has been displayed.
\item $L$ is the residual ledger, listing the dense-open obligations already met by the constructed thread and the finite evidence that each listed obligation is met inside the chosen successor ball.
\item $H$ records componentwise $\hsame$ transport for the Baire prefix, dense-open schedule, complete-metric handoff, stream windows, regular readback, real seal, residual ledger, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a residual request to the finite Baire prefix, dense-open schedule, completion handoff, stream windows, rational readback, real seal, and residual ledger rows.
\item $P$ is the $\Pkg$ provenance over $\BaireGenericResidualUp$, $\BaireSpaceUp$, $\BaireCategoryUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BaireGenericResidualUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through the rows $B,D,M,S,W,R,E,L,H,C,P,N$. It has no coordinate for countable choice, a host intersection point, quotient equality of streams, or completeness of an ambient real line.
\end{definition}

\begin{theorem}[Baire generic residual NameCert obligations]
\label{thm:baire-generic-residual-namecert-obligations}
For every accepted $\BaireGenericResidualUp$ carrier $G=(B,D,M,S,W,R,E,L,H,C,P,N)$, the local $\NameCert_{\BaireGenericResidualUp}$ surface consists exactly of carrier admission for the Baire prefix, dense-open schedule, complete-metric handoff, StreamName windows, window ledger, RegSeqRat readback, Real seal, residual ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every accepted residual read must remain inside these rows and may not inspect countable-choice selectors, host intersection points, quotient stream equality, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:baire-generic-residual-carrier}. The analytic rows are $B,D,M,S,W,R,E,L$, and the structural rows are $H,C,P,N$.

The dense-open work is confined to $D,W,L$. The schedule row names the finite dense requests, the window ledger records the predecessor and successor ball observations, and the residual ledger records that each displayed request has been met by the current thread.

The completion work is confined to $M,S,R,E$. The complete-metric row supplies the handoff for the nested thread, the stream schedule selects the inspected windows, the regular-rational row reads the centers and radii, and the real seal is downstream from that route.

Transport, replay, provenance, and local naming preserve the same displayed packet. Since no listed row stores a countable-choice selector, a host intersection point, quotient equality of streams, or ambient Real completeness, the displayed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Baire generic residual thread handoff]
\label{thm:baire-generic-residual-thread-handoff}
Every $\RealUp$ seal exported by an accepted $\BaireGenericResidualUp$ carrier factors through the constructive residual thread
$$
\BaireSpaceUp
\longmapsto
\BaireCategoryUp
\longmapsto
\CompleteMetricUp
\longmapsto
\StreamNameUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The handoff records residual membership only through the finite residual ledger $L$ and exports no host intersection point, countable-choice enumeration, quotient stream equality, or separate ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the carrier route in \autoref{def:baire-generic-residual-carrier}. The terminal real row $E$ is downstream from the Baire prefix $B$, the dense-open schedule $D$, the complete-metric handoff $M$, the inspected stream windows $S,W$, and the regular rational readback $R$.

The residual claim is ledgered, not selected. Each displayed dense-open obligation is recorded in $L$ with the finite successor-ball evidence currently consumed by the route, so the proof never chooses a point outside the displayed thread.

Finally replay the route through $C$ and transport it through $H$. The provenance row $P$ and local naming row $N$ name the same finite packet, so the exported $\RealUp$ seal has no hidden coordinate from which countable choice, a host intersection point, quotient stream equality, or ambient completeness can be read.
\end{proof}

\closureat{BaireGenericResidualUp}{seedStr}

\begin{closurestatus}{\BaireGenericResidualUp}
  \constructivestory{A $\BaireGenericResidualUp$ packet is generated from a BaireSpace prefix, a BaireCategory dense-open schedule, a CompleteMetric handoff, StreamName windows, RegSeqRat readback, a Real seal, a residual ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:baire-generic-residual-carrier}, \autoref{thm:baire-generic-residual-namecert-obligations}, and \autoref{thm:baire-generic-residual-thread-handoff} seed the constructive residual-point route over BaireSpaceUp, BaireCategoryUp, CompleteMetricUp, StreamNameUp, RegSeqRatUp, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim countable choice, host intersection points, quotient stream equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-open schedule exactness, complete-metric handoff, StreamName window readback, RegSeqRat readback, Real seal discipline, residual-ledger stability, transport, replay, provenance, and local naming for BEDC.Derived.BaireGenericResidualUp.}
\end{closurestatus}
