\chapter{A Concrete Naming Certificate for $\LocatedCauchyFilterCompletionUp$}
\label{ch:concrete-instances-located-cauchy-filter-completion-namecert}
\origin{human}

Following Bishop and Bridges and Kelley, the $\LocatedCauchyFilterCompletionUp$ packet records the constructive L10 completion route in which a located Cauchy filter is completed through finite BEDC rows rather than through quotient selection or host real equality. It sits over the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the located-filter boundary of \autoref{ch:concrete-instances-located-cauchy-filter-namecert}, the completion interface of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}, the stream-name windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names a non-quotient located-filter completion packet that separated-completion and uniform-completion consumers can read without importing countable choice, selected limits, or ambient completeness.

\begin{definition}[Located Cauchy filter completion carrier]
\label{def:located-cauchy-filter-completion-carrier}
A $\LocatedCauchyFilterCompletionUp$ carrier is a finite $\BHist$ packet
$$
Q=(F,L,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the source $\CauchyFilterUp$ row, naming the filter base, finite tail requests, and Cauchy refinement ledger.
\item $L$ is the $\LocatedCauchyFilterUp$ row, exposing the locatedness decisions through finite interval and apartness reads.
\item $W$ is the $\StreamNameUp$ window schedule used to inspect the completion name at the requests opened by $F$ and $L$.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the inspected windows and to the regular rational approximants accepted by the filter route.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling comparison slack, refinement radius, and located interval separation.
\item $E$ is the terminal $\RealUp$ seal reached only after the displayed $F,L,W,R,D$ route has been exposed.
\item $H$ records componentwise $\hsame$ transport for the filter, locatedness, window, readback, dyadic, real-seal, replay, provenance, and local-name rows.
\item $C$ records displayed $\Cont$ replay from a completion request through the located filter, stream window, regular readback, dyadic tolerance, and terminal real-seal rows.
\item $P$ is the $\Pkg$ provenance over $\LocatedCauchyFilterCompletionUp$, $\CauchyFilterUp$, $\LocatedCauchyFilterUp$, $\CauchyFilterCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCauchyFilterCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,L,W,R,D,E,H,C,P,N$. It has no coordinate for quotient filters, selected representatives, countable choice, ambient completeness of $\RealUp$, or host equality of completed real names.
\end{definition}

\begin{theorem}[Located Cauchy filter completion NameCert obligations]
\label{thm:located-cauchy-filter-completion-namecert-obligations}
For every accepted $\LocatedCauchyFilterCompletionUp$ carrier
$$
Q=(F,L,W,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedCauchyFilterCompletionUp}$ surface consists exactly of carrier admission, source Cauchy-filter readback, located-filter exposure, stream-window inspection, regular rational readback, dyadic tolerance accounting, terminal real-seal discipline, componentwise transport, displayed replay, provenance, and local naming. Every completion-facing consumer must read the finite route
$$
\CauchyFilterUp \longmapsto \LocatedCauchyFilterUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp
$$
before it may export the completion row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-cauchy-filter-completion-carrier}. The projection exposes the source Cauchy-filter row, the locatedness row, the window schedule, the regular rational readback, the dyadic tolerance ledger, the terminal real seal, and the structural rows.

The completion route is then forced by the displayed order. The filter row $F$ supplies the finite Cauchy requests, the located row $L$ supplies interval and apartness decisions, and the window row $W$ identifies the inspected name fragments.

The readback and seal rows do not add a quotient coordinate. The row $R$ reads the regular rational approximants under the dyadic budget $D$, and only then may the terminal real row $E$ be exposed.

Finally transport and replay use $H$ and $C$, while $P$ and $N$ source and name the same packet. Since no carrier coordinate stores quotient filters, selected representatives, countable choice, or ambient completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Located Cauchy filter completion real-seal handoff]
\label{thm:located-cauchy-filter-completion-real-seal-handoff}
Every $\RealUp$ read handed off by an accepted $\LocatedCauchyFilterCompletionUp$ packet must pass through the source $\CauchyFilterUp$ row, the located $\LocatedCauchyFilterUp$ row, the $\StreamNameUp$ inspection schedule, the $\RegSeqRatUp$ readback row, and the $\DyadicRatCoreUp$ tolerance ledger before reaching the terminal seal $E$. The handoff supplies the finite real-name boundary consumed by $\CauchyFilterCompletionUp$ descendants; it does not supply a quotient of filters, a selected limit, countable choice, host real equality, or completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:located-cauchy-filter-completion-namecert-obligations}. They already order every completion-facing read through $F,L,W,R,D,E$ before any consumer sees the real-seal row.

The located-filter row is the boundary that prevents an unlocated completion read. A consumer must expose the interval and apartness decisions carried by $L$ before it can use the stream windows and regular rational approximants.

The real-seal handoff is therefore finite. The terminal row $E$ is reached only through the displayed filter, locatedness, window, readback, and tolerance rows, and the structural rows $H,C,P,N$ only transport, replay, source, and name that same route.

The excluded analytic principles are absent from the carrier. Thus downstream separated-completion or uniform-completion packets may consume this chapter as a located finite completion boundary, not as a quotient construction or a host completeness theorem.
\end{proof}

\closureat{LocatedCauchyFilterCompletionUp}{seedStr}

\begin{closurestatus}{\LocatedCauchyFilterCompletionUp}
  \constructivestory{A $\LocatedCauchyFilterCompletionUp$ packet is generated from a source CauchyFilter row, a LocatedCauchyFilter row, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-cauchy-filter-completion-carrier}, \autoref{thm:located-cauchy-filter-completion-namecert-obligations}, and \autoref{thm:located-cauchy-filter-completion-real-seal-handoff} seed the non-quotient located-filter completion boundary over CauchyFilterUp, LocatedCauchyFilterUp, CauchyFilterCompletionUp, StreamNameUp, RegSeqRatUp, DyadicRatCoreUp, and RealUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filters, selected representatives, countable choice, host real equality, completeness of RealUp, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove carrier admission, located-filter exposure, window inspection, regular rational readback, dyadic tolerance accounting, real-seal handoff, transport, replay, provenance, and ledger non-escape.}
\end{closurestatus}
