\chapter{A Concrete Naming Certificate for $\BishopUniformCompletionTheoremUp$}
\label{ch:concrete-instances-bishop-uniform-completion-theorem-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\BishopUniformCompletionTheoremUp$ packet records the theorem-level route from displayed uniform Cauchy data to the regular completion handoff. It consumes the uniform-space carrier of \autoref{ch:concrete-instances-uniformspace-namecert}, the Cauchy-filter tail surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the finite-window naming route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, and the universal completion row of \autoref{ch:concrete-instances-regular-cauchy-completion-universal-namecert}. The packet names a finite theorem carrier for uniform completion consumers without quotient completion objects, selected representatives, countable choice, host real equality, or ambient completeness.

\begin{definition}[Bishop uniform completion theorem carrier]
\label{def:bishop-uniform-completion-theorem-carrier}
A $\BishopUniformCompletionTheoremUp$ carrier is a finite $\BHist$ packet
$$
U=(X,F,S,R,E,V,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the $\UniformSpaceUp$ carrier row, recording the displayed source points, entourage requests, refinement reads, and separatedness boundary available to the theorem consumer.
\item $F$ is the $\CauchyFilterUp$ tail-data row, storing the finite filter-base and tail-stability evidence read inside the same uniform carrier.
\item $S$ is the $\StreamNameUp$ finite-window row, presenting the inspected Cauchy-filter observations as bounded observation windows rather than as an infinite chosen representative.
\item $R$ is the $\RegSeqRatUp$ readback row, translating the inspected windows into regular rational names through the displayed dyadic tolerance route.
\item $E$ is the $\RealUp$ seal row, recording the terminal real-name observations produced from the regular rational readback.
\item $V$ is the $\RegularCauchyCompletionUniversalUp$ handoff row, naming the extension-and-uniqueness surface available to completion consumers after the source, tail, window, readback, and seal rows have all been read.
\item $H$ records componentwise $\hsame$ transport for the uniform carrier, Cauchy-filter tail data, finite windows, regular rational readback, Real seal, universal handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
X,F,S,R,E,V \longmapsto \NameCert_{\BishopUniformCompletionTheoremUp}.
$$
\item $P$ is the $\Pkg$ provenance row over $\BishopUniformCompletionTheoremUp$, $\UniformSpaceUp$, $\CauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularCauchyCompletionUniversalUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ dependency rows.
\item $N$ is the local $\NameCert_{\BishopUniformCompletionTheoremUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, selected completion representatives, a countable-choice schedule, host real equality, or an ambient completeness theorem.
\end{definition}

\begin{theorem}[Bishop uniform completion theorem NameCert obligations]
\label{thm:bishop-uniform-completion-theorem-namecert-obligations}
For an accepted $\BishopUniformCompletionTheoremUp$ carrier
$$
U=(X,F,S,R,E,V,H,C,P,N),
$$
the local $\NameCert_{\BishopUniformCompletionTheoremUp}$ surface consists exactly of carrier admission for the displayed rows, uniform-space admission for $X$, Cauchy-filter tail stability for $F$, finite-window inspection for $S$, regular rational readback for $R$, terminal Real sealing for $E$, regular-completion universal handoff for $V$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$. No obligation may be discharged by quotient completion, selected representatives, countable choice, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:bishop-uniform-completion-theorem-carrier}. The accepted packet displays the uniform carrier, the Cauchy-filter tail data, the finite windows, the regular rational readback, the Real seal, and the universal handoff.

The theorem route begins with $X$ and $F$. The uniform row fixes the entourage discipline, while the Cauchy-filter row supplies only finite tail evidence inside that discipline. There is no independent coordinate for a quotient completion object or a selected filter representative.

The observation route then passes through $S$, $R$, and $E$. Finite windows are read as regular rational names and then sealed as displayed Real rows, so the certificate never replaces the readback with host real equality, countable choice, or ambient completeness.

Finally $V$ is the only completion-facing exit. The rows $H,C,P,N$ transport, replay, source, and name the same finite route, so every local obligation is accounted for by the displayed rows and no hidden completion principle can enter the packet.
\end{proof}

\begin{theorem}[Bishop uniform completion theorem uniform handoff]
\label{thm:bishop-uniform-completion-theorem-uniform-handoff}
Every theorem consumer of an accepted $\BishopUniformCompletionTheoremUp$ carrier factors through the displayed route
$$
\UniformSpaceUp \longmapsto \CauchyFilterUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp \longmapsto \RegularCauchyCompletionUniversalUp.
$$
The consumer first reads the uniform carrier, then the Cauchy-filter tail row, then the finite-window observations, then the regular rational readback, then the Real seal, and only then the regular-completion universal handoff.
\end{theorem}
\begin{proof}
Begin with the accepted carrier $U$. The only uniform data available to a theorem consumer is $X$, and the only Cauchy data is the tail row $F$ read inside that same uniform carrier.

The consumer must next inspect the finite windows $S$ and their regular rational readback $R$. These rows supply the named observations from which the Real seal $E$ is produced; no selected representative or countable-choice schedule is present in the carrier.

The completion-facing handoff $V$ can be read only after $X,F,S,R,E$ have been opened. Since the remaining rows merely transport, replay, source, and locally name this route, every theorem consumer factors through the stated chain and cannot bypass it by invoking quotient completion, host real equality, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every $\BishopUniformCompletionTheoremUp$ theorem read factors through one UniformSpace carrier row, one CauchyFilter tail row, one StreamName finite-window row, one RegSeqRat readback row, one Real seal row, one RegularCauchyCompletionUniversal handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{uniformspace, cauchyfilter, streamname, regseqrat, real, regular-cauchy-completion-universal: $\BishopUniformCompletionTheoremUp$ is not bijective to any listed sibling because it jointly carries the source uniform structure, Cauchy-filter tail evidence, finite windows, regular rational readback, Real seal, universal completion handoff, and the transport/replay/provenance rows binding them into a theorem-level completion certificate.}

\closureat{BishopUniformCompletionTheoremUp}{seedStr}

\begin{closurestatus}{\BishopUniformCompletionTheoremUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-uniform-completion-theorem-carrier}, \autoref{thm:bishop-uniform-completion-theorem-namecert-obligations}, and \autoref{thm:bishop-uniform-completion-theorem-uniform-handoff} seed the uniform completion theorem route over a uniform carrier, Cauchy-filter tail row, finite windows, regular rational readback, Real seal, universal handoff, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient completion, selected representatives, countable choice, host real equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform-space admission, Cauchy-filter tail stability, finite-window inspection, regular rational readback, Real sealing, universal completion handoff, transport, replay, provenance, and local naming for BEDC.Derived.BishopUniformCompletionTheoremUp.}
  \constructivestory{A $\BishopUniformCompletionTheoremUp$ packet is generated from one UniformSpace carrier row, one CauchyFilter tail-data row, one StreamName finite-window row, one RegSeqRat readback row, one Real seal row, one RegularCauchyCompletionUniversal handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
