\chapter{A Concrete Naming Certificate for $\PrecompactUniformUp$}
\label{ch:concrete-instances-precompact-uniform-namecert}
\origin{human}

Following Bourbaki and Kelley on precompact uniform spaces, the $\PrecompactUniformUp$ packet records the finite total-bounded uniform route used by the L10 completion spine. It consumes the entourage carrier of \autoref{ch:concrete-instances-uniformspace-namecert}, the finite covering comparison of \autoref{ch:concrete-instances-totallybounded-namecert}, the Cauchy request surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, and the completion handoff of \autoref{ch:concrete-instances-uniformcompletion-namecert}. The packet names a precompactness route without importing open-cover compactness, quotient completions, selected limits, countable choice, or ambient completeness.

\begin{definition}[PrecompactUniform carrier]
\label{def:precompact-uniform-carrier}
A $\PrecompactUniformUp$ carrier is a finite $\BHist$ packet
$$
U=(X,E,F,T,Q,K,S,R,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\UniformSpaceUp$ source row, recording the source points, entourage requests, refinement rows, and separatedness boundary available to the packet.
\item $E$ is the entourage ledger row. It lists the finitely inspected entourages and the refinement comparisons used before any covering row is read.
\item $F$ is the finite cover row. For each displayed entourage request it stores the finite family of centers and the witness that the inspected source points are covered at that entourage.
\item $T$ is the $\TotallyBoundedUp$ comparison row, binding the finite cover data to the sibling total-bounded carrier surface.
\item $Q$ is the $\CauchyFilterUp$ request row, recording only those Cauchy requests whose entourage demands have already passed through $E,F,T$.
\item $K$ is the $\UniformCompletionUp$ handoff row for completion consumers that receive the precompact uniform packet after the finite cover and Cauchy request rows have been displayed.
\item $S$ is the $\StreamNameUp$ finite-window row for the inspected request windows.
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row for the finite entourage and readback comparisons.
\item $H$ records componentwise $\hsame$ transport for the uniform source, entourage ledger, finite cover row, total-bounded comparison, Cauchy requests, completion handoff, finite windows, readbacks, dyadic tolerance rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay through
$$
X,E,F,T,Q,K,S,R,D \longmapsto \NameCert_{\PrecompactUniformUp}.
$$
\item $P$ is the $\Pkg$ provenance over $\PrecompactUniformUp$, $\UniformSpaceUp$, $\TotallyBoundedUp$, $\CauchyFilterUp$, $\UniformCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\PrecompactUniformUp}$ row.
\end{enumerate}
The carrier has no coordinate for open-cover compactness, quotient completion equality, selected Cauchy representatives, countable choice, host equality, or ambient completeness.
\end{definition}

\begin{theorem}[PrecompactUniform NameCert obligations]
\label{thm:precompact-uniform-namecert-obligations}
For an accepted $\PrecompactUniformUp$ carrier
$$
U=(X,E,F,T,Q,K,S,R,D,H,C,P,N),
$$
the local $\NameCert_{\PrecompactUniformUp}$ surface consists exactly of carrier admission for the displayed rows, uniform-space admission for $X$, entourage-ledger exactness for $E$, finite-cover exactness for $F$, total-bounded comparison through $T$, Cauchy-filter request admission through $Q$, uniform-completion handoff through $K$, finite-window and readback inspection through $S,R,D$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:precompact-uniform-carrier}. It displays the uniform source, entourage ledger, finite cover row, total-bounded comparison, Cauchy request row, completion handoff, finite windows, readbacks, dyadic tolerances, and structural rows.

The analytic route begins with $X,E,F,T$. A consumer first reads the uniform-space surface, then the inspected entourages, then the finite cover witnesses, and only then the total-bounded comparison row.

The completion-facing route is downstream of $Q,K,S,R,D$. Cauchy requests, completion handoffs, finite windows, regular readbacks, and dyadic tolerances are therefore bound to the same finite cover data.

Finally $H,C,P,N$ transport, replay, source, and locally name the same packet. Since no excluded object is a coordinate of the carrier, the displayed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[PrecompactUniform completion handoff]
\label{thm:precompact-uniform-completion-handoff}
Every $\UniformCompletionUp$ consumer of an accepted $\PrecompactUniformUp$ carrier first reads the $\UniformSpaceUp$ source row, the entourage ledger, the finite cover row, the $\TotallyBoundedUp$ comparison row, and the $\CauchyFilterUp$ request row before it may inspect the completion handoff $K$. The handoff is a finite L10 completion route through the displayed rows, not an open-cover compactness theorem or a quotient completion object.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:precompact-uniform-namecert-obligations}. They place the completion handoff after the uniform source, entourage, finite-cover, total-bounded, and Cauchy request rows.

The finite windows $S$, readbacks $R$, and dyadic tolerances $D$ are read on the same route. They provide the observed request data needed by completion consumers without selecting a limit or quotienting Cauchy names.

Transport and replay through $H$ and $C$ preserve the row order. Thus every completion consumer reaches $K$ only through the displayed precompact uniform packet and cannot bypass it by invoking compactness, choice, or ambient completeness.
\end{proof}

\begin{theorem}[PrecompactUniform nonescape]
\label{thm:precompact-uniform-nonescape}
An accepted $\PrecompactUniformUp$ packet exports only the displayed rows
$$
X,E,F,T,Q,K,S,R,D,H,C,P,N .
$$
No downstream completion, compactness, or Cauchy-filter consumer can obtain open-cover compactness, quotient completion equality, selected representatives, countable-choice schedules, host equality, or ambient completeness from the packet.
\end{theorem}
\begin{proof}
Use \autoref{def:precompact-uniform-carrier} to list the available coordinates. The only analytic rows are the uniform source, entourage ledger, finite cover data, total-bounded comparison, Cauchy request, completion handoff, finite windows, readbacks, and dyadic tolerance rows.

Use \autoref{thm:precompact-uniform-completion-handoff}. Completion-facing reads are confined to those rows before the handoff is exposed.

The structural rows $H,C,P,N$ only transport, replay, source, and name the finite route. Because the excluded compactness and completion principles are absent from the carrier, no consumer can project them from an accepted packet.
\end{proof}

\closureat{PrecompactUniformUp}{seedStr}
\begin{closurestatus}{\PrecompactUniformUp}
  \constructivestory{A $\PrecompactUniformUp$ packet is generated from a UniformSpace source row, entourage ledger rows, finite cover rows, a TotallyBounded comparison row, CauchyFilter request rows, a UniformCompletion handoff, StreamName finite windows, RegSeqRat readback, DyadicRatCore tolerance rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:precompact-uniform-carrier}, \autoref{thm:precompact-uniform-namecert-obligations}, \autoref{thm:precompact-uniform-completion-handoff}, and \autoref{thm:precompact-uniform-nonescape} seed the finite precompact uniform route for L10 completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, quotient completion, selected representatives, countable choice, host equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, entourage exactness, finite-cover exactness, total-bounded comparison, Cauchy-filter request admission, completion handoff, readback, tolerance, transport, replay, provenance, and local naming for BEDC.Derived.PrecompactUniformUp.}
\end{closurestatus}
