\chapter{A Concrete Naming Certificate for $\HausdorffUniformityUp$}
\label{ch:concrete-instances-hausdorff-uniformity-namecert}
\origin{human}

Following Bourbaki and Kelley, the $\HausdorffUniformityUp$ packet records the separated uniformity interface used by completion and uniqueness consumers before any quotient completion or representative choice is available. It sits between the entourage surface of \autoref{ch:concrete-instances-uniformspace-namecert}, the zero-distance classifier discipline of \autoref{ch:concrete-instances-separatedmetric-namecert}, the metric completion route of \autoref{ch:concrete-instances-metriccompletion-namecert}, and the Cauchy-filter completion boundary of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}. The packet names the finite Hausdorff-uniformity boundary as BEDC data; it does not identify host points, select completion representatives, or import a quotient completion.

\begin{definition}[Hausdorff uniformity carrier]
\label{def:hausdorff-uniformity-carrier}
A $\HausdorffUniformityUp$ carrier is a finite $\BHist$ packet
$$
H=(U,E,D,Z,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the underlying $\UniformSpaceUp$ row, including the finite entourage basis, diagonal-membership ledger, and refinement surface read by downstream consumers.
\item $E$ is the uniform entourage row, recording the displayed entourages through which all separation and completion-facing comparisons must pass.
\item $D$ is the diagonal separation row, witnessing that indistinguishability by the displayed entourages reaches the local classifier rather than host equality.
\item $Z$ is the zero-distance handoff row, routing metric-generated separated reads through the $\SeparatedMetricUp$ classifier before a completion consumer inspects uniqueness.
\item $T$ records componentwise $\hsame$ transport for $U,E,D,Z$ and for the local continuation, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
U,E\longmapsto D\longmapsto Z .
$$
\item $P$ is the $\Pkg$ provenance over $\HausdorffUniformityUp$, $\UniformSpaceUp$, $\SeparatedMetricUp$, $\MetricCompletionUp$, $\CauchyFilterCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HausdorffUniformityUp}$ row.
\end{enumerate}
The classifier of an accepted packet compares observations only through $U,E,D,Z,T,C,P,N$. It has no coordinate for quotient uniform completions, host equality of points, selected representatives, countable choice, ambient completeness, or bridge data.
\end{definition}

\begin{theorem}[Hausdorff uniformity NameCert obligations]
\label{thm:hausdorff-uniformity-namecert-obligations}
For every accepted $\HausdorffUniformityUp$ carrier
$$
H=(U,E,D,Z,T,C,P,N),
$$
the local $\NameCert_{\HausdorffUniformityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the uniform-space row, entourage row, diagonal separation row, zero-distance handoff row, transport, replay, provenance, and local naming rows;
\item entourage stability, requiring every separated comparison to begin with the displayed entourage basis and refinement data of $U,E$;
\item diagonal separation, requiring all indistinguishability-to-classifier reads to pass through $D$ rather than through host equality;
\item completion-facing zero-distance handoff, requiring metric or filter completion consumers to read $Z$ before using uniqueness data;
\item componentwise transport and displayed replay through $T,C$;
\item ledger non-escape, excluding quotient completions, host point equality, selected representatives, countable choice, ambient completeness, Lean verification, and bridge checking.
\end{enumerate}
No local NameCert obligation is stored outside these six rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:hausdorff-uniformity-carrier}. The accepted tuple displays exactly the uniform-space row, the entourage row, the diagonal separation row, the zero-distance handoff, and the structural rows.

Entourage stability follows from the order of the carrier. The rows $U,E$ supply the displayed entourage basis and refinement data before diagonal separation can be read, so a consumer cannot replace finite uniform evidence by host equality of points.

The diagonal separation row $D$ is the only exported route from uniform indistinguishability to the local classifier. The zero-distance handoff row $Z$ then records the metric-generated or completion-facing comparison surface without adding a quotient completion or a representative selector.

Finally inspect $T,C,P,N$. Transport is componentwise, replay follows the displayed route, and provenance plus local naming mention only the rows listed in the carrier. Hence the packet exports no quotient completion, host equality, selected representative, countable-choice schedule, ambient completeness theorem, Lean verification, or bridge checking.
\end{proof}

\closureat{HausdorffUniformityUp}{seedStr}

\begin{closurestatus}{\HausdorffUniformityUp}
  \constructivestory{A $\HausdorffUniformityUp$ packet is generated from a UniformSpace row, a displayed entourage row, a diagonal separation row, a zero-distance handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-uniformity-carrier} and \autoref{thm:hausdorff-uniformity-namecert-obligations} seed the finite Hausdorff-uniformity interface over uniform-space, entourage, diagonal separation, zero-distance handoff, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, host equality of points, selected representatives, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, entourage stability, diagonal separation, completion-facing zero-distance handoff, componentwise transport, replay, provenance, and ledger non-escape for BEDC.Derived.HausdorffUniformityUp.}
\end{closurestatus}
