\chapter{A Concrete Naming Certificate for $\RegularCauchyPositivePartUp$}
\label{ch:concrete-instances-regular-cauchy-positive-part-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyPositivePartUp$ packet reads the constructive positive part of a regular Cauchy real name through the finite identity $x^{+}=max(x,0)$. The certificate sits beside the absolute-value, maximum, and minimum surfaces of \autoref{ch:concrete-instances-regularcauchyabs-namecert}, \autoref{ch:concrete-instances-regularcauchymax-namecert}, and \autoref{ch:concrete-instances-regularcauchymin-namecert}; it uses the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. The downstream real lattice comparison surface of \autoref{ch:concrete-instances-real-min-max-namecert} consumes the same finite order-operation discipline. The packet does not import trichotomy, host real order, quotient stream equality, selected limits, or ambient completeness.

\begin{definition}[RegularCauchyPositivePart carrier]
\label{def:regular-cauchy-positive-part-carrier}
A $\RegularCauchyPositivePartUp$ carrier is a finite $\BHist$ packet
$$
P=(X,Z,W,D_X,D_Z,A,M,R,E,H,C,L,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $X$ is the source $\RegSeqRatUp$ regular rational Cauchy name row.
\item $Z$ is the displayed zero regular Cauchy row over the same rational readback surface.
\item $W$ is the shared $\StreamNameUp$ window schedule used to observe $X$ and $Z$ at the same finite precision requests.
\item $D_X$ and $D_Z$ are the displayed $\DyadicRatCoreUp$ endpoint-and-tolerance rows read from the shared window schedule.
\item $A$ is the $\RegularCauchyAbsUp$ compatibility row for the absolute-value route attached to $X$.
\item $M$ is the $\RegularCauchyMaxUp$ row for the finite maximum route $max(X,Z)$.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from the positive-part windows and the displayed tolerance ledger.
\item $E$ is the $\RealUp$ seal row reached only after the readback row $R$ has been exposed.
\item $H$ records componentwise $\hsame$ transport for the source, zero row, shared window, dyadic rows, absolute-value compatibility, maximum row, readback, seal, provenance, and local name.
\item $C$ records the displayed $\Cont$ routes from the source and zero rows through the shared windows, dyadic observations, maximum row, readback, and real seal.
\item $L$ records $\Pkg$ provenance over $\RegularCauchyPositivePartUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyAbsUp$, $\RegularCauchyMaxUp$, $\RegularCauchyMinUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RegularCauchyPositivePartUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through $X,Z,W,D_X,D_Z,A,M,R,E,H,C,L,N$. It has no coordinate for trichotomy of completed reals, host real order, quotient stream equality, selected limits, or a $\RealUp$ completeness principle.
\end{definition}

\begin{theorem}[RegularCauchyPositivePart NameCert obligations]
\label{thm:regular-cauchy-positive-part-namecert-obligations}
For every accepted $\RegularCauchyPositivePartUp$ carrier $P=(X,Z,W,D_X,D_Z,A,M,R,E,H,C,L,N)$, the local $\NameCert_{\RegularCauchyPositivePartUp}$ surface consists exactly of source $\RegSeqRatUp$ admission, displayed zero-row admission, shared $\StreamNameUp$ window exposure, $\DyadicRatCoreUp$ tolerance observations, $\RegularCauchyAbsUp$ compatibility, the $\RegularCauchyMaxUp$ positive-part row, $\RegSeqRatUp$ readback, $\RealUp$ seal boundary, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed packet $P$. The coordinates expose the source regular name, the zero row, the shared finite windows, dyadic endpoint-and-tolerance rows, the absolute-value compatibility row, the maximum row, the regular readback, the real seal, and the structural rows.

The operation obligation is the finite lattice route. The maximum surface of \autoref{ch:concrete-instances-regularcauchymax-namecert} supplies the row $M$ for $max(X,Z)$, while the absolute-value surface of \autoref{ch:concrete-instances-regularcauchyabs-namecert} supplies the compatibility row $A$ used by consumers that read the equivalent absolute-value factorization. The minimum surface of \autoref{ch:concrete-instances-regularcauchymin-namecert} supplies the sibling lower-part comparison discipline, so the positive-part packet remains aligned with the same displayed-window lattice family.

The readback and seal obligations are then the finite handoffs through $\RegSeqRatUp$ and $\RealUp$. The rows $H,C,L,N$ transport, replay, source, and name this same route without adding trichotomy, host real order, quotient streams, selected limits, or ambient completeness.
\end{proof}

\begin{theorem}[RegularCauchyPositivePart Real seal handoff]
\label{thm:regular-cauchy-positive-part-real-seal-handoff}
Every $\RealUp$ or real-lattice consumer of an accepted $\RegularCauchyPositivePartUp$ carrier reaches the positive-part seal row $E$ only after the shared source and zero windows, the dyadic tolerance rows, the $\RegularCauchyMaxUp$ row $M$, and the $\RegSeqRatUp$ readback row $R$ have been exposed. The route is compatible with the $\RealMinMaxUp$ lattice boundary of \autoref{ch:concrete-instances-real-min-max-namecert}, but it exports no host order comparison, trichotomy witness, quotient stream equality, selected limit, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with a $\RealUp$ or lattice-facing consumer. By \autoref{def:regular-cauchy-positive-part-carrier}, the only real-facing endpoint in the packet is the seal row $E$, and that row is downstream of the readback row $R$.

The readback is downstream of the finite maximum row $M$. The maximum route consumes the source row $X$, the displayed zero row $Z$, the shared window schedule $W$, and the dyadic tolerance rows $D_X,D_Z$ before the positive-part value can be named.

Finally compare the route with the real min/max boundary. The sibling $\RealMinMaxUp$ surface consumes displayed real seals through finite min/max rows, so this packet hands it a positive-part seal already produced by regular-Cauchy windows, dyadic tolerance rows, readback, transport, replay, provenance, and local naming. Since none of the excluded analytic principles occurs as a coordinate of $P$, no consumer can reach the positive part by a non-displayed route.
\end{proof}

\falsifiablePrediction{An accepted $\RegularCauchyPositivePartUp$ consumer that exports a positive-part seal without first reading the source RegSeqRat row, displayed zero row, shared StreamName windows, DyadicRatCore tolerance rows, RegularCauchyMax row, RegSeqRat readback, RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert row refutes the carrier surface.}

\independenceWitness{regular Cauchy positive part: $\RegularCauchyPositivePartUp$ binds a source RegSeqRat row, displayed zero row, shared StreamName windows, DyadicRatCore tolerance observations, RegularCauchyAbs compatibility, RegularCauchyMax readback, RegSeqRat handoff, RealUp seal, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ into one finite lattice-operation packet.}

\closureat{RegularCauchyPositivePartUp}{seedStr}

\begin{closurestatus}{\RegularCauchyPositivePartUp}
  \constructivestory{A $\RegularCauchyPositivePartUp$ packet is generated from one RegSeqRat source row, a displayed zero row, shared StreamName windows, DyadicRatCore endpoint observations, a RegularCauchyAbs compatibility row, a RegularCauchyMax row, a RegSeqRat readback row, a RealUp seal row, componentwise transport, continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-positive-part-carrier}, \autoref{thm:regular-cauchy-positive-part-namecert-obligations}, and \autoref{thm:regular-cauchy-positive-part-real-seal-handoff} seed the finite constructive positive-part route through regular Cauchy maximum, readback, and RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, trichotomy on completed real names, host real order, quotient stream equality, selected limits, ambient completeness, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, zero-row admission, window exposure, dyadic tolerance rows, RegularCauchyMax handoff, RealUp seal boundary, transport stability, provenance, and non-escape for the same finite packet.}
\end{closurestatus}
