\chapter{A Concrete Naming Certificate for $\MetaCICConfluenceDiamondBoundaryUp$}
\label{ch:concrete-instances-metacic-confluence-diamond-boundary-namecert}
\origin{ai}

The $\MetaCICConfluenceDiamondBoundaryUp$ packet realizes the confluence audit boundary of \autoref{ch:metacic-confluence-audit-map} as a finite diamond-frontier object. It sits beside the critical-path carrier of \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, the confluence audit packet of \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, the local diamond witness of \autoref{ch:concrete-instances-metacic-local-diamond-witness-namecert}, the residual checker of \autoref{ch:concrete-instances-metacic-confluence-residual-checker-namecert}, and the subject-reduction discharge socket of \autoref{ch:concrete-instances-subject-reduction-discharge-socket-namecert}. The packet names local peaks, candidate joins, residual frontiers, substitution boundaries, bounded checks, and obstruction rows without claiming full confluence or subject reduction.

\falsifiablePrediction{Every accepted $\MetaCICConfluenceDiamondBoundaryUp$ confluence-frontier read exposes local-peak, candidate-join, residual-frontier, substitution-boundary, bounded-check, obstruction, transport, replay, provenance, and local NameCert rows before any diamond-boundary handoff is consumed.}

\independenceWitness{metaciccriticalpath, metacicconfluenceauditpacket, metacic-local-diamond-witness, metacic-confluence-residual-checker, subject-reduction-discharge-socket: the critical-path carrier records dependency pressure without a per-diamond boundary; the confluence audit packet records global audit rows without bounded local frontier status; the local-diamond witness records a peak and candidate join without residual-checker obstruction retention; the residual checker records bounded residual windows without the subject-reduction socket boundary; and the discharge socket records typing-side rows without confluence peak data. None is bijective to $\MetaCICConfluenceDiamondBoundaryUp$.}

\begin{definition}[MetaCIC confluence-diamond boundary carrier]
\label{def:metacic-confluence-diamond-boundary-carrier}
A $\MetaCICConfluenceDiamondBoundaryUp$ carrier is a finite $\BHist$ packet
$$
D=(K,J,R,S,B,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the local-peak row, naming the source term and the two outgoing reduction or parallel-reduction observations.
\item $J$ is the candidate-join row, recording the proposed common reduct and the two route requests into it.
\item $R$ is the residual-frontier row, listing residual redex descendants, binder-depth exposure, and branch-local frontier checks.
\item $S$ is the substitution-boundary row, naming the substitution-sensitive input that remains visible whenever the candidate join is not an unconditional diamond.
\item $B$ is the bounded-check row, recording the finite closedness, support, branch-compatibility, and variable-escape checks applied to the displayed peak.
\item $O$ is the obstruction row, naming the still-open endpoints: unrestricted substitution compatibility, premise-free closed parallel diamond, arbitrary closed Church--Rosser, subject reduction, evaluator equality, and kernel consistency.
\item $H$ records componentwise $\hsame$ transport for local peaks, candidate joins, residual frontiers, substitution boundaries, bounded checks, obstruction rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a confluence query through $K,J,R,S,B,O,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MetaCICConfluenceDiamondBoundaryUp$, $\MetaCICCriticalPathUp$, $\MetaCICConfluenceAuditPacketUp$, $\MetaCICLocalDiamondWitnessUp$, $\MetaCICConfluenceResidualCheckerUp$, $\SubjectReductionDischargeSocketUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetaCICConfluenceDiamondBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,J,R,S,B,O,H,C,P,N$. It has no coordinate for a global confluence theorem, a subject-reduction theorem, unrestricted substitution compatibility, quotient equality of terms, evaluator equality, or kernel consistency.
\end{definition}

\begin{theorem}[MetaCIC confluence-diamond boundary obligations]
\label{thm:metacic-confluence-diamond-boundary-obligations}
For every accepted $\MetaCICConfluenceDiamondBoundaryUp$ carrier
$$
D=(K,J,R,S,B,O,H,C,P,N),
$$
the local $\NameCert_{\MetaCICConfluenceDiamondBoundaryUp}$ surface consists exactly of local-peak exposure through $K$, candidate-join exposure through $J$, residual-frontier exposure through $R$, substitution-boundary retention through $S$, bounded-check exposure through $B$, obstruction retention through $O$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-confluence-diamond-boundary-carrier}. Rows $K,J,R,S,B,O$ are the diamond-facing data, and rows $H,C,P,N$ are the structural certificate data.

The local peak and candidate join must be read together. Row $K$ displays the source and the two outgoing observations, while $J$ records only a proposed common reduct and route requests rather than a global Church--Rosser theorem.

The residual and substitution boundaries remain visible next. Rows $R$ and $S$ expose residual descendants, binder-depth data, and substitution-sensitive inputs, while $B$ records the bounded finite checks that have actually been performed.

Finally $O$ keeps the open endpoints named, and $H,C,P,N$ transport, replay, source, and name the same packet. Since no carrier coordinate contains full confluence, subject reduction, unrestricted substitution compatibility, quotient term equality, evaluator equality, or kernel consistency, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[MetaCIC confluence-diamond boundary handoff]
\label{thm:metacic-confluence-diamond-boundary-handoff}
Every confluence consumer of an accepted $\MetaCICConfluenceDiamondBoundaryUp$ carrier factors through
$$
K,J,R,S,B,O,H,C,P,N
$$
before it may export a diamond-boundary handoff. The handoff may feed the confluence audit packet, local-diamond witness, residual checker, critical-path packet, or subject-reduction discharge socket named above, but it does not fill the substitution boundary, prove subject reduction, prove full confluence, decide evaluator equality, or establish kernel consistency.
\end{theorem}
\begin{proof}
Begin with the obligation surface of \autoref{thm:metacic-confluence-diamond-boundary-obligations}. It forces every consumer read through the peak row, candidate join row, residual frontier, substitution boundary, bounded checks, and obstruction row before the structural rows are consumed.

The sibling handoffs preserve that boundary. The audit packet may read the confluence-frontier data, the local-diamond witness may read the peak and join rows, the residual checker may read $R,S,B,O$, the critical-path packet may read the obstruction pressure, and the discharge socket may read only the subject-reduction-facing boundary.

No sibling read adds a hidden theorem row to $D$. Therefore the handoff remains finite diamond-boundary data and cannot be cited as unrestricted substitution compatibility, subject reduction, full confluence, evaluator equality, or kernel consistency.
\end{proof}

Lean follow-up for \texttt{BEDC.Derived.MetaCICConfluenceDiamondBoundaryUp} requires $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ TasteGate instances at the displayed carrier surface.

\closureat{MetaCICConfluenceDiamondBoundaryUp}{seedStr}

\begin{closurestatus}{\MetaCICConfluenceDiamondBoundaryUp}
  \constructivestory{A $\MetaCICConfluenceDiamondBoundaryUp$ packet is generated from local-peak rows, candidate-join rows, residual-frontier rows, substitution-boundary rows, bounded-check rows, obstruction rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-confluence-diamond-boundary-carrier}, \autoref{thm:metacic-confluence-diamond-boundary-obligations}, and \autoref{thm:metacic-confluence-diamond-boundary-handoff} seed the finite confluence-diamond boundary packet for MetaCIC audit consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close unrestricted substitution compatibility, full confluence, subject reduction, evaluator equality, quotient equality of terms, kernel consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, local-peak exposure, candidate-join exactness, residual-frontier coverage, substitution-boundary retention, bounded-check exactness, obstruction retention, TasteGate nontriviality, FieldFaithful coverage, transport, replay, provenance, and local naming for BEDC.Derived.MetaCICConfluenceDiamondBoundaryUp.}
\end{closurestatus}
