\chapter{A Concrete Naming Certificate for $\StopTrpFaceRankDeficiencyUp$}
\label{ch:concrete-instances-stop-trp-face-rank-deficiency-namecert}
\origin{ai}

The $\StopTrpFaceRankDeficiencyUp$ packet realizes the local suffix-support
rank theorem of \autoref{def:philosophy-bedc-local-support-rank} and
\autoref{thm:philosophy-bedc-stop-rank-deficiency} as finite BEDC NameCert
data. It consumes the six-coordinate codon source of
\autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the boundary
classifier of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert},
the coverage-rank surface of
\autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, and the
codon lift-orbit classifier of
\autoref{ch:concrete-instances-codon-lift-orbit-classifier-namecert}. The
packet records the stop/Trp face as the local two-coordinate square whose
proper-support vertices are the stop row and whose full-support corner is the
retained Trp row; it is not a biological mechanism, stochastic fitness model,
quotient codon semantics, or hidden global translation table.

\begin{definition}[Stop/Trp face rank-deficiency carrier]
\label{def:stop-trp-face-rank-deficiency-carrier}
A $\StopTrpFaceRankDeficiencyUp$ carrier is a finite $\BHist$ packet
$$
F=(W,B,C,O,S,R,L,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ source-window row exposing the
six-bit codon coordinates.
\item $B$ is the $\DnaWindowSixBoundaryTileUp$ stop/Trp boundary row,
selecting the $\mathrm{U}+\mathrm{RR}$ face
$\{\mathrm{UAA},\mathrm{UAG},\mathrm{UGA},\mathrm{UGG}\}$.
\item $C$ is the $\SixBoundaryTileCoverageUp$ coverage row that keeps the
visible boundary support inside the displayed tile surface.
\item $O$ is the $\CodonLiftOrbitClassifierUp$ row that records the finite
orbit-readback context for the same codon window.
\item $S$ is the local suffix-support table row based at $\mathrm{UAA}$,
with supports $\varnothing$, $\{f_3\}$, $\{f_2\}$, and
$\{f_2,f_3\}$.
\item $R$ is the rank-deficiency row, recording that stop vertices are
exactly the rows whose support is a proper subset of $\{f_2,f_3\}$.
\item $L$ is the ledger row separating the full-support $\mathrm{UGG}$ corner
from the three proper-support stop vertices.
\item $H$ records componentwise $\hsame$ transport for source windows,
boundary tiles, coverage rows, orbit-classifier rows, suffix-support rows,
rank rows, ledger rows, replay, provenance, and local naming.
\item $K$ records displayed $\Cont$ replay from a stop-face query through
$W,B,C,O,S,R,L,H$.
\item $P$ is the $\Pkg$ provenance over $\StopTrpFaceRankDeficiencyUp$,
$\CodonSixBitWindowUp$, $\DnaWindowSixBoundaryTileUp$,
$\SixBoundaryTileCoverageUp$, $\CodonLiftOrbitClassifierUp$,
\autoref{thm:philosophy-bedc-stop-rank-deficiency}, $\BHist$, $\hsame$,
$\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StopTrpFaceRankDeficiencyUp}$ row.
\end{enumerate}
The classifier accepts a stop-face rank read only through
$W,B,C,O,S,R,L,H,K,P,N$. It has no coordinate for a hidden genetic-code table,
probabilistic dynamics, quotient codon equality, biological causation, or a
global semantic equivalence.
\end{definition}

\begin{theorem}[Stop/Trp face rank-deficiency NameCert obligations]
\label{thm:stop-trp-face-rank-deficiency-namecert-obligations}
For every accepted $\StopTrpFaceRankDeficiencyUp$ carrier
$F=(W,B,C,O,S,R,L,H,K,P,N)$, the local
$\NameCert_{\StopTrpFaceRankDeficiencyUp}$ surface consists exactly of the
following finite obligations:
\begin{enumerate}
\item carrier admission for the codon-window, boundary-tile, coverage,
lift-orbit, suffix-support, rank-deficiency, ledger, transport, replay,
provenance, and local naming rows;
\item face exposure, requiring the stop/Trp read to pass through $W$ and $B$
before any support rank is inspected;
\item coverage and orbit compatibility, requiring $C$ and $O$ to preserve the
same displayed codon-window context as $W$ and $B$;
\item suffix-rank exactness, requiring $S$ and $R$ to classify
$\mathrm{UAA}$, $\mathrm{UAG}$, and $\mathrm{UGA}$ as proper-support rows and
$\mathrm{UGG}$ as the unique full-support row;
\item separated ledger discipline, requiring $L$ to keep stop legality and
Trp retention as different displayed rows;
\item structural preservation through $H,K,P,N$;
\item ledger non-escape, excluding hidden biological tables, stochastic
mechanisms, quotient codon equality, global semantics, and external
translation classifiers.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from
\autoref{def:stop-trp-face-rank-deficiency-carrier}. The accepted packet
displays the codon-window source, boundary-tile classifier, coverage route,
lift-orbit context, suffix-support table, rank-deficiency row, ledger row,
and structural rows.

The face exposure clause forces the local read to begin with $W$ and $B$.
Thus the rank table is attached to the displayed stop/Trp face, not to an
unrecorded biological table.

Coverage and orbit compatibility are downstream checks on the same finite
window. The rows $C$ and $O$ preserve the boundary support and orbit-readback
context before $S$ and $R$ classify local suffix support.

The rank exactness row is the finite table of
\autoref{def:philosophy-bedc-local-support-rank}. Proper subsets of
$\{f_2,f_3\}$ give $\mathrm{UAA}$, $\mathrm{UAG}$, and $\mathrm{UGA}$, while
the full support gives $\mathrm{UGG}$. The ledger row $L$ records this
separation without collapsing the full-support corner into the stop row.

Finally $H,K,P,N$ preserve, replay, source, and name only these displayed
rows. Since no excluded object is a carrier coordinate, the listed obligations
exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Stop/Trp face local rank-deficiency route]
\label{thm:stop-trp-face-rank-deficiency-local-route}
Let $F=(W,B,C,O,S,R,L,H,K,P,N)$ be an accepted
$\StopTrpFaceRankDeficiencyUp$ carrier. Every accepted stop-face rank read
factors through the finite route
$$
\CodonSixBitWindowUp \longmapsto \DnaWindowSixBoundaryTileUp
\longmapsto \SixBoundaryTileCoverageUp
\longmapsto \CodonLiftOrbitClassifierUp
\longmapsto S,R,L,H,K,P,N .
$$
Along this route the vertices $\mathrm{UAA}$, $\mathrm{UAG}$, and
$\mathrm{UGA}$ are exactly the proper-support rows of $\{f_2,f_3\}$, while
$\mathrm{UGG}$ is the unique full-support corner. The packet exports no hidden
code table, stochastic mechanism, quotient codon semantics, or global
translation classifier.
\end{theorem}
\begin{proof}
Start with an accepted stop-face rank read. The carrier requires the read to
consume the source window $W$ and the boundary tile $B$, so the four codons are
the displayed $\mathrm{U}+\mathrm{RR}$ face.

The coverage row $C$ and lift-orbit row $O$ keep the same finite codon-window
context visible. They do not replace the local face by a global biological
semantics.

Now read $S$ and $R$. By
\autoref{thm:philosophy-bedc-stop-rank-deficiency}, the proper-support
vertices in the two suffix coordinates are precisely
$\mathrm{UAA}$, $\mathrm{UAG}$, and $\mathrm{UGA}$, and the remaining
$\mathrm{UGG}$ corner has full support.

The ledger row $L$ records that separation, and $H,K,P,N$ transport, replay,
source, and name the route. No excluded semantic or quotient object appears in
the carrier, so the read cannot escape the displayed rank-deficiency packet.
\end{proof}

\falsifiablePrediction{A $\StopTrpFaceRankDeficiencyUp$ consumer that classifies $\mathrm{UAA}$, $\mathrm{UAG}$, or $\mathrm{UGA}$ without displaying the suffix-support row $S$ and rank row $R$ is not reading an accepted packet of this chapter.}

\independenceWitness{codon-six-bit-window, dna-window-six-boundary-tile, six-boundary-tile-coverage, codon-lift-orbit-classifier: $\StopTrpFaceRankDeficiencyUp$ is not bijective to any listed sibling because it jointly carries the source window, stop/Trp boundary face, coverage row, orbit-readback context, suffix-support table, rank-deficiency classifier, separated ledger, transport, replay, provenance, and local naming.}

The Lean TasteGate route for \texttt{BEDC.Derived.StopTrpFaceRankDeficiencyUp.TasteGate} must provide explicit $\Nontrivial\ \StopTrpFaceRankDeficiencyUp$ and $\FieldFaithful\ \StopTrpFaceRankDeficiencyUp$ instances preserving $W,B,C,O,S,R,L,H,K,P,N$ as separate displayed fields.

\closureat{StopTrpFaceRankDeficiencyUp}{seedStr}

\begin{closurestatus}{\StopTrpFaceRankDeficiencyUp}
  \constructivestory{A $\StopTrpFaceRankDeficiencyUp$ packet is generated from CodonSixBitWindowUp source rows, DnaWindowSixBoundaryTileUp stop/Trp boundary rows, SixBoundaryTileCoverageUp coverage rows, CodonLiftOrbitClassifierUp orbit rows, suffix-support rows, rank-deficiency rows, a separated ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stop-trp-face-rank-deficiency-carrier}, \autoref{thm:stop-trp-face-rank-deficiency-namecert-obligations}, and \autoref{thm:stop-trp-face-rank-deficiency-local-route} seed the finite stop/Trp face rank-deficiency packet over the local suffix-support theorem.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, biological causation, stochastic fitness modeling, quotient codon equality, hidden translation tables, or global semantics.}
  \upgradepath{Obligation closure requires checked carrier admission, face exposure, coverage and orbit compatibility, suffix-rank exactness, separated ledger discipline, Nontrivial StopTrpFaceRankDeficiencyUp, and FieldFaithful StopTrpFaceRankDeficiencyUp for BEDC.Derived.StopTrpFaceRankDeficiencyUp.}
\end{closurestatus}
