\chapter{A Concrete Naming Certificate for $\ReflexiveBanachUp$}
\label{ch:concrete-instances-reflexive-banach-namecert}
\origin{human}

Following Banach and Alaoglu, the $\ReflexiveBanachUp$ packet records the finite double-dual evaluation window that functional-analysis consumers may inspect before any weak compactness conclusion is read. It sits beside the finite weak-star dual-ball route of \autoref{ch:concrete-instances-banach-alaoglu-namecert}, the weak observation surface of \autoref{ch:concrete-instances-weak-topology-namecert}, the norm ledger of \autoref{ch:concrete-instances-norm-namecert}, the Hilbert comparison surface of \autoref{ch:concrete-instances-hilbert-namecert}, and the functional-analysis carrier of \autoref{ch:concrete-instances-functionalanalysis-namecert}. The packet names only displayed Banach, norm, dual-window, double-dual evaluation, weak-topology, bounded-ball, transport, replay, provenance, and local naming rows; it does not assert full Eberlein--Smulian, select weak cluster points, import quotient dual equality, or use choice over all bounded nets.

\begin{definition}[ReflexiveBanach finite double-dual carrier]
\label{def:reflexive-banach-carrier}
A $\ReflexiveBanachUp$ carrier is a finite $\BHist$ packet
$$
R=(B,N,D,E,W,A,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the Banach carrier row, read through the displayed $\BanachUp$ and $\FunctionalAnalysisUp$ surfaces.
\item $N$ is the norm row, recording the finite norm estimates used by source, dual, and ball consumers through $\NormUp$.
\item $D$ is the dual-window row, listing the finitely many bounded-linear-functional observations allowed in the current packet.
\item $E$ is the double-dual evaluation row, recording the canonical evaluation of displayed source endpoints against the functionals named by $D$.
\item $W$ is the weak-topology readback row, sending those finite scalar evaluations to the $\WeakTopologyUp$ observation surface.
\item $A$ is the bounded-ball ledger, recording the finite norm-bound rows whose weak-compactness handoff is visible to later consumers.
\item $H$ records componentwise $\hsame$ transport for the Banach carrier, norm row, dual windows, double-dual evaluations, weak readbacks, bounded-ball ledgers, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from Banach admission through norm control, dual-window evaluation, weak readback, and bounded-ball handoff.
\item $P$ is the $\Pkg$ provenance over $\ReflexiveBanachUp$, $\BanachUp$, $\NormUp$, $\WeakTopologyUp$, $\BanachAlaogluUp$, $\HilbertUp$, $\FunctionalAnalysisUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\ReflexiveBanachUp}$ row.
\end{enumerate}
The carrier has no coordinate for a completed host double dual, quotient equality of dual functionals, a selected weak cluster point, a countable-choice family of balls, or an unrestricted compactness theorem.
\end{definition}

\begin{theorem}[ReflexiveBanach NameCert obligations]
\label{thm:reflexive-banach-namecert-obligations}
For every accepted $\ReflexiveBanachUp$ carrier $R=(B,N,D,E,W,A,H,C,P,L)$, the local $\NameCert_{\ReflexiveBanachUp}$ surface consists exactly of carrier admission for $B$, double-dual evaluation stability for $E$, weak topology compatibility for $W$, bounded-ball readback for $A$, and no-choice ledger nonescape for the structural rows $H,C,P,L$. Every accepted read must expose the Banach carrier, norm row, finite dual window, evaluation row, weak readback row, and bounded-ball ledger before local naming is consumed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:reflexive-banach-carrier}. The rows $B,N,D,E,W,A,H,C,P,L$ are the complete visible inventory, so carrier admission and local naming can only use those coordinates.

The double-dual evaluation obligation is finite. Each evaluation in $E$ is tied to a source endpoint from $B$ and a bounded functional from $D$, with norm control read through $N$; componentwise transport through $H$ preserves the same displayed evaluation row.

Weak topology compatibility follows by reading $W$ through the finite scalar observation surface of \autoref{ch:concrete-instances-weak-topology-namecert}. The bounded-ball ledger $A$ is downstream of the same norm and evaluation rows, and the Banach--Alaoglu sibling supplies only the finite dual-ball window cited in the provenance row.

Finally $C,P,L$ replay, source, and name that same packet. Since no row stores a selected cluster point, quotient dual equality, host double-dual equality, or a choice family over all bounded balls, the no-choice ledger cannot escape the displayed finite route.
\end{proof}

\begin{theorem}[ReflexiveBanach weak compactness handoff]
\label{thm:reflexive-banach-weak-compactness-handoff}
Every weak-compactness-facing consumer of an accepted $\ReflexiveBanachUp$ packet must factor through the finite route
$$
B,N,D,E,W,A \longmapsto H,C,P,L .
$$
The consumer may cite $\BanachAlaogluUp$ only through the finite dual-window provenance, may cite $\WeakTopologyUp$ only through the scalar readback row $W$, and may cite $\HilbertUp$ or $\FunctionalAnalysisUp$ only through the displayed source and norm rows. It receives no selected weakly convergent subnet, no quotient dual-space equality, no host compactness theorem, and no choice-based traversal of the bounded ball.
\end{theorem}
\begin{proof}
Begin with the bounded-ball ledger. The row $A$ is read after the Banach carrier $B$ and norm row $N$, so every ball-facing request is already confined to displayed norm estimates over the accepted carrier.

Next expose the dual-window and evaluation rows. The row $D$ lists only finitely many bounded-functional observations, and $E$ evaluates displayed source endpoints against those observations before the weak-topology row $W$ can be consumed.

The weak readback is therefore a finite scalar route. By \autoref{ch:concrete-instances-weak-topology-namecert} and \autoref{ch:concrete-instances-banach-alaoglu-namecert}, downstream compactness vocabulary can only repackage the finite weak and weak-star windows already present in $D,E,W,A$.

Transport, replay, provenance, and local naming preserve this route through $H,C,P,L$. The absence of selector, quotient, host compactness, and choice-family coordinates prevents the handoff from becoming a nonconstructive weak compactness principle.
\end{proof}

\falsifiablePrediction{Every accepted $\ReflexiveBanachUp$ packet exposes a Banach carrier, norm row, finite dual-window row, double-dual evaluation row, weak-topology readback row, bounded-ball ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert before any weak compactness consumer can read the packet.}

\independenceWitness{banach-alaoglu, weak-topology, norm, hilbert, functionalanalysis: $\ReflexiveBanachUp$ is not bijective to any listed sibling because it jointly carries double-dual evaluation rows and bounded-ball weak-readback ledgers over a Banach source while refusing selected weak cluster points and quotient dual equality.}

\closureat{ReflexiveBanachUp}{seedStr}

\begin{closurestatus}{\ReflexiveBanachUp}
  \constructivestory{A $\ReflexiveBanachUp$ packet is generated from a Banach carrier, norm row, finite dual-window row, double-dual evaluation row, weak-topology readback row, bounded-ball ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:reflexive-banach-carrier}, \autoref{thm:reflexive-banach-namecert-obligations}, and \autoref{thm:reflexive-banach-weak-compactness-handoff} seed the finite double-dual and bounded-ball weak-readback certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Eberlein--Smulian, selected weak cluster points, quotient dual equality, host double-dual equality, full weak compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, double-dual evaluation stability, weak topology compatibility, bounded-ball readback, no-choice ledger nonescape, transport, replay, provenance, and local naming for BEDC.Derived.ReflexiveBanachUp.}
\end{closurestatus}
