\chapter{A Concrete Naming Certificate for $\SeparatedCompletionFunctorUp$}
\label{ch:concrete-instances-separated-completion-functor-namecert}
\origin{human}

Following Bishop and Bridges and Mac Lane, the $\SeparatedCompletionFunctorUp$ packet records the functoriality certificate for separated completion as finite BEDC NameCert data. It sits after the separated-completion surface of \autoref{ch:concrete-instances-separatedcompletion-namecert}, the public Cauchy reflector of \autoref{ch:concrete-instances-cauchycompletionreflector-namecert}, the metric-completion handoff of \autoref{ch:concrete-instances-metriccompletion-namecert}, and the L10 finite-name route through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names the source-to-target transport of a uniformly continuous map through separated completion without importing quotient completions, chosen limits, host function extensionality, countable choice, ambient completeness, or bridge checking.

\begin{definition}[Separated completion functor carrier]
\label{def:separated-completion-functor-carrier}
A $\SeparatedCompletionFunctorUp$ carrier is a finite $\BHist$ packet
$$
F=(M,N,f,S,T,R,L,W,Q,A,H,C,P,E)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric row, naming the source carrier, metric comparison surface, and finite Cauchy-input budget.
\item $N$ is the target metric row, naming the target carrier, metric comparison surface, and completion-facing output budget.
\item $f$ is the source map row, recording the displayed uniformly continuous map data consumed by the completion route.
\item $S$ is the source $\SeparatedCompletionUp$ row, read from the source metric before any completed source name is transported.
\item $T$ is the target $\SeparatedCompletionUp$ row, read from the target metric before any completed target name is exposed.
\item $R$ is the $\CauchyCompletionReflectorUp$ row, recording the reflector handoff that turns source Cauchy data into a completion-facing read.
\item $L$ is the $\MetricCompletionUp$ row, recording the metric-completion consumer surface through which the target completion read is delivered.
\item $W$ is the $\StreamNameUp$ local observation row attached to source and target completion names.
\item $Q$ is the $\RegSeqRatUp$ local tolerance row consumed after $W$ and before any terminal real-name seal.
\item $A$ is the $\RealUp$ local seal row reached only through $W,Q$ and the displayed separated-completion rows.
\item $H$ records componentwise $\hsame$ transport for source metric data, target metric data, the source map, separated-completion rows, reflector and metric-completion rows, local L10 rows, replay, provenance, and naming.
\item $C$ records displayed $\Cont$ replay from a source completion request through $M,N,f,S,T,R,L,W,Q,A,H,P,E$.
\item $P$ is the $\Pkg$ provenance over $\SeparatedCompletionFunctorUp$, $\SeparatedCompletionUp$, $\CauchyCompletionReflectorUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $E$ is the local $\NameCert_{\SeparatedCompletionFunctorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,N,f,S,T,R,L,W,Q,A,H,C,P,E$. It has no coordinate for quotient completion equality, selected limit representatives, host function extensionality, countable choice, ambient completeness of either completed metric, or a standard bridge.
\end{definition}

\begin{theorem}[Separated completion functor NameCert obligations]
\label{thm:separated-completion-functor-namecert-obligations}
For every accepted $\SeparatedCompletionFunctorUp$ carrier
$$
F=(M,N,f,S,T,R,L,W,Q,A,H,C,P,E),
$$
the local $\NameCert_{\SeparatedCompletionFunctorUp}$ surface consists exactly of source metric admission, target metric admission, source map admission, separated-completion exposure on both sides, Cauchy-reflector exposure, metric-completion exposure, StreamName observation, RegSeqRat tolerance readback, Real seal readback, componentwise transport, displayed replay, package provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-completion-functor-carrier}. The rows $M,N,f$ expose the source metric, target metric, and map data before any completion-facing consumer reads the packet.

The separated-completion rows come next. Rows $S$ and $T$ keep the source and target completion surfaces separated before the reflector row $R$ and the metric-completion row $L$ are consumed.

The local numerical route is finite. The StreamName row $W$, RegSeqRat row $Q$, and Real row $A$ display the L10 readback used by completion consumers, while $H,C,P,E$ transport, replay, source, and name the same route.

Since no carrier coordinate contains quotient completion equality, a chosen limit representative, host function extensionality, countable choice, ambient completeness, or a bridge theorem, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Separated completion functor Cauchy-reflector route]
\label{thm:separated-completion-functor-cauchy-reflector-route}
Let $F=(M,N,f,S,T,R,L,W,Q,A,H,C,P,E)$ be an accepted $\SeparatedCompletionFunctorUp$ carrier. Every completion-facing read of the transported map factors through the route
$$
M,N,f,S,T,R,L,W,Q,A,H,C,P,E
$$
before a target completion name is exported. In particular, the Cauchy-reflector row $R$ and metric-completion row $L$ are read only after both separated-completion rows $S,T$ have been displayed, and the local $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows are read only as the terminal L10 route of that same packet.
\end{theorem}
\begin{proof}
Start with a transported-map request for an accepted carrier. The source and target metric rows $M,N$ and the source map row $f$ are the only input coordinates available to the request.

Read the separated-completion rows $S,T$ before any completion-facing handoff. This forces equality-facing and completion-facing consumers to remain on the separated surfaces carried by the packet.

The Cauchy reflector and metric completion handoffs are then $R$ and $L$. Their consumers receive the local L10 route only through $W,Q,A$, so the exported target completion name remains attached to the displayed source map, separated-completion rows, transport, replay, provenance, and local naming.

Because the carrier contains no quotient completion class, selected limit, host function-extensionality proof, countable-choice selector, ambient-completeness row, or bridge theorem, no completion-facing read can bypass the named route.
\end{proof}

\falsifiablePrediction{Every accepted $\SeparatedCompletionFunctorUp$ transport read displays source metric, target metric, source map, source separated-completion, target separated-completion, CauchyCompletionReflector, MetricCompletion, StreamName, RegSeqRat, Real, transport, replay, provenance, and local NameCert rows before a target completion name is exported.}

\independenceWitness{separatedcompletion, cauchycompletionreflector, metriccompletion, streamname, regseqrat, real: the separated completion functor packet is not bijective to any listed sibling because it jointly carries a source metric row, target metric row, source map row, separated-completion rows on both sides, reflector and metric-completion handoffs, the local L10 readback route, transport, replay, provenance, and local naming.}

\closureat{SeparatedCompletionFunctorUp}{seedStr}

\begin{closurestatus}{\SeparatedCompletionFunctorUp}
  \constructivestory{A $\SeparatedCompletionFunctorUp$ packet is generated from source metric data, target metric data, a source map row, separated-completion rows on both sides, CauchyCompletionReflectorUp and MetricCompletionUp handoffs, StreamNameUp observations, RegSeqRatUp tolerance readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:separated-completion-functor-carrier}, \autoref{thm:separated-completion-functor-namecert-obligations}, and \autoref{thm:separated-completion-functor-cauchy-reflector-route} seed the finite functorial separated-completion route from a source map through separated completions and the L10 completion readback.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected limits, host function extensionality, countable choice, ambient completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked source metric admission, target metric admission, source map admission, separated-completion exposure on both sides, Cauchy-reflector handoff, metric-completion handoff, StreamName observation, RegSeqRat tolerance readback, Real seal readback, transport, replay, provenance, and local naming for BEDC.Derived.SeparatedCompletionFunctorUp.}
\end{closurestatus}
