\chapter{A Concrete Naming Certificate for $\CompactModulusSelectorUp$}
\label{ch:concrete-instances-compact-modulus-selector-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis and the Heine--Cantor finite-net proof, the $\CompactModulusSelectorUp$ packet records the finite selector route that turns compact-metric total boundedness and pointwise continuity data into a reusable uniform-modulus certificate. It sits over the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the total-boundedness finite-net interface of \autoref{ch:concrete-instances-totallybounded-namecert}, the continuous-map row of \autoref{ch:concrete-instances-continuousmap-namecert}, and the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. Its L10 real-facing reads pass through the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet names finite-net modulus selection as displayed BEDC data; it does not assert open-cover compactness, countable choice, a selected infinite net, host function equality, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[CompactModulusSelector carrier]
\label{def:compact-modulus-selector-carrier}
A $\CompactModulusSelectorUp$ carrier is a finite $\BHist$ packet
$$
S=(K,T,F,U,D,W,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the accepted $\CompactMetricUp$ source row. It records the compact metric carrier and its displayed metric observation surface.
\item $T$ is the $\TotallyBoundedUp$ finite-net row read from $K$ at the requested dyadic tolerance scale.
\item $F$ is the $\ContinuousMapUp$ graph and pointwise-continuity row whose local moduli are inspected only at the displayed net centers.
\item $U$ is the candidate $\UniformModulusUp$ row exported to downstream uniform-continuity consumers.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling the source mesh, target error budget, and triangle comparison.
\item $W$ is the $\StreamNameUp$ finite-window row naming the inspected net-center and point-name windows.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the finite metric and image-distance observations.
\item $A$ is the terminal $\RealUp$ seal row reached only after $D,W,R$ have displayed the requested estimates.
\item $H$ records componentwise $\hsame$ transport for compact metric, total-boundedness, continuous-map, uniform-modulus, dyadic, window, readback, seal, continuation, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from a uniform-modulus request through the compact finite-net selection route and then into the exported modulus row.
\item $P$ is the $\Pkg$ provenance over $\CompactMetricUp$, $\TotallyBoundedUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CompactModulusSelectorUp}$ row.
\end{enumerate}
The carrier has no coordinate for open-cover compactness, a choice function over all covers, selected infinite subnet data, host equality of maps, trichotomy, quotient completion, or ambient real completeness.
\end{definition}

\begin{theorem}[CompactModulusSelector NameCert obligations]
\label{thm:compact-modulus-selector-namecert-obligations}
For every accepted $\CompactModulusSelectorUp$ carrier $S=(K,T,F,U,D,W,R,A,H,C,P,N)$, the local $\NameCert_{\CompactModulusSelectorUp}$ surface consists exactly of carrier admission for the compact metric source, total-bounded finite net, continuous-map row, uniform-modulus export, dyadic tolerance ledger, finite windows, regular readback, Real seal, transport, continuation, provenance, and local naming rows. Any consumer that reads the exported modulus must consume the finite-net row $T$, the pointwise continuity row $F$, and the dyadic comparison row $D$ before $U$ is visible. The packet exports no open-cover compactness, countable choice, host map equality, selected infinite net, trichotomy, quotient completion, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-modulus-selector-carrier}. The listed coordinates are exactly the compact metric, total-boundedness, continuous-map, uniform-modulus, dyadic, window, readback, Real-seal, transport, replay, provenance, and local naming rows.

Replay $C$. A modulus request first reads the compact metric source $K$, then the finite-net row $T$, then the continuous-map row $F$ at the displayed net centers. The dyadic ledger $D$, finite windows $W$, and regular readback $R$ provide the requested source and target estimates before the terminal seal $A$ is consumed.

The exported row $U$ is therefore a finite-net modulus row. Transport by $H$ preserves only the displayed coordinates, while $P$ and $N$ package and name the same route, so none of the excluded principles appears as a hidden obligation.
\end{proof}

\begin{theorem}[CompactModulusSelector finite-net selection]
\label{thm:compact-modulus-selector-finite-net-selection}
Let $S=(K,T,F,U,D,W,R,A,H,C,P,N)$ be an accepted $\CompactModulusSelectorUp$ packet. Every exported $\UniformModulusUp$ read factors through the finite route
$$
K,T,F,D,W,R,A \longmapsto U,H,C,P,N .
$$
The finite net is read from $\TotallyBoundedUp$ inside the $\CompactMetricUp$ source, the local continuity data are read from $\ContinuousMapUp$ at the displayed net centers, and the dyadic tolerance ledger supplies the comparison budget. The route preserves all rows $K,T,F,U,D,W,R,A,H,C,P,N$ and exports no open-cover compactness, countable choice, selected infinite net, host equality of functions, trichotomy, quotient completion, or ambient real completeness.
\end{theorem}
\begin{proof}
Start from a consumer of the uniform-modulus row. Carrier admission exposes $U$ only as a row of the packet named in \autoref{def:compact-modulus-selector-carrier}.

Use the continuation row $C$ to replay the finite selection route. The compact metric source $K$ supplies the ambient metric data, $T$ supplies the finite net, and $F$ supplies the local continuity data at the displayed centers.

The tolerance and readback rows $D,W,R,A$ then certify the comparison budget before $U$ is exported. Since transport, provenance, and naming are confined to $H,C,P,N$, the handoff preserves the listed rows and cannot export any of the excluded choice, open-cover, equality, or completeness data.
\end{proof}

\closureat{CompactModulusSelectorUp}{seedStr}

\begin{closurestatus}{\CompactModulusSelectorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-modulus-selector-carrier}, \autoref{thm:compact-modulus-selector-namecert-obligations}, and \autoref{thm:compact-modulus-selector-finite-net-selection} seed the finite-net modulus selector route over compact metric, total-bounded, continuous-map, uniform-modulus, dyadic, window, readback, Real-seal, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, countable choice, selected infinite nets, host function equality, trichotomy, quotient completion, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net selection, pointwise-continuity inspection, dyadic tolerance comparison, uniform-modulus export, and structural nonescape for BEDC.Derived.CompactModulusSelectorUp.}
  \constructivestory{A $\CompactModulusSelectorUp$ packet is generated from a CompactMetric row, a TotallyBounded finite-net row, a ContinuousMap pointwise-continuity row, a UniformModulus export row, dyadic tolerance data, finite windows, regular readback, a Real seal, componentwise transport, continuation replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
