\chapter{A Concrete Naming Certificate for $\MengerNobelingEmbeddingUp$}
\label{ch:concrete-instances-menger-nobeling-embedding-namecert}
\origin{human}

Following Menger and Nobeling, the $\MengerNobelingEmbeddingUp$ packet records a finite-dimensional metric embedding handoff as BEDC NameCert data. It sits after the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the compact finite-net surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the distance-function route of \autoref{ch:concrete-instances-kuratowski-embedding-namecert}, the tolerance-indexed net row of \autoref{ch:concrete-instances-finite-epsilon-net-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite coordinate route needed by embedding consumers; it is not a host Euclidean space, not a selected infinite coordinate family, not a quotient completion, and not an ambient dimension theorem.

\begin{definition}[Menger--Nobeling embedding carrier]
\label{def:menger-nobeling-embedding-carrier}
A $\MengerNobelingEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
E=(M,K,Q,F,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source $\MetricUp$ row whose point classifier and distance classifier are read by the embedding packet.
\item $K$ is the $\CompactMetricUp$ or compact finite-metric handoff row supplying the finite cover and compact inspection data used by the coordinate budget.
\item $Q$ is the $\KuratowskiEmbeddingUp$ distance-function row that turns source-distance observations into displayed real-valued coordinate observations.
\item $F$ is the $\FiniteEpsilonNetUp$ row that records the inspected center bundle, tolerance, and coverage witnesses used to choose a finite coordinate window.
\item $R$ is the $\RealUp$ readback row for the displayed coordinate values and finite separation inequalities.
\item $H$ records componentwise $\hsame$ transport for the metric source, compact handoff, Kuratowski row, finite-net row, real readbacks, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from metric-distance reads through $K,Q,F,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MengerNobelingEmbeddingUp$, $\MetricUp$, $\CompactMetricUp$, $\KuratowskiEmbeddingUp$, $\FiniteEpsilonNetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MengerNobelingEmbeddingUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,K,Q,F,R,H,C,P,N$. It has no coordinate for a host Euclidean carrier, a selected infinite coordinate family, quotient completion, open-cover compactness, countable choice, or an ambient dimension principle.
\end{definition}

\begin{theorem}[Menger--Nobeling embedding NameCert obligations]
\label{thm:menger-nobeling-embedding-namecert-obligations}
For every accepted $\MengerNobelingEmbeddingUp$ carrier $E=(M,K,Q,F,R,H,C,P,N)$, the local $\NameCert_{\MengerNobelingEmbeddingUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed metric source, compact handoff, Kuratowski distance-function row, finite epsilon-net row, real coordinate readback, transport, replay, provenance, and local naming row;
\item metric-source exposure, requiring every source point and distance read to enter through $M$;
\item compact finite-net exposure, requiring every finite coordinate budget to be read through the compact row $K$ and the finite-net row $F$;
\item Kuratowski coordinate handoff, requiring every displayed coordinate observation to pass through $Q$ before its $\RealUp$ readback in $R$ is consumed;
\item finite separation stability, requiring the same $F,Q,R$ rows to witness the finite coordinate separation read under componentwise transport $H$;
\item non-escape, excluding host Euclidean carriers, selected infinite coordinate families, quotient completions, open-cover compactness, countable choice, and ambient dimension principles from the local certificate.
\end{enumerate}
No Menger--Nobeling embedding obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:menger-nobeling-embedding-carrier}. The only analytic rows are the metric source $M$, the compact handoff $K$, the Kuratowski distance-function row $Q$, the finite-net row $F$, and the real coordinate readback row $R$.

The compact coordinate budget is finite because it is read through $K$ and $F$. The compact row supplies the finite inspection context, while the finite epsilon-net row supplies the displayed center bundle, tolerance, and coverage witnesses used by the coordinate window.

The coordinate values are then forced through the Kuratowski route. The row $Q$ exposes distance-function observations, and $R$ reads those observations through the terminal Real boundary before any separation claim is exported.

Finally, $H,C,P,N$ preserve and name the same route. Since the carrier has no Euclidean host, infinite coordinate-family selector, quotient-completion row, open-cover compactness row, choice schedule, or ambient dimension row, none of those objects can become a local NameCert obligation.
\end{proof}

\begin{theorem}[Menger--Nobeling embedding finite coordinate handoff]
\label{thm:menger-nobeling-embedding-finite-coordinate-handoff}
Every $\MetricUp$, $\CompactMetricUp$, $\KuratowskiEmbeddingUp$, $\FiniteEpsilonNetUp$, or $\RealUp$ consumer of an accepted $\MengerNobelingEmbeddingUp$ carrier must read the finite route
$$
M,K,Q,F,R,H,C,P,N .
$$
Thus a finite-dimensional embedding request reaches coordinate data only after the metric source, compact finite-net budget, Kuratowski distance-function observations, and real readbacks are visible. The handoff exports no host Euclidean carrier, selected infinite coordinate family, quotient completion, open-cover compactness, countable choice, or ambient dimension principle.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $E=(M,K,Q,F,R,H,C,P,N)$. A consumer can enter the packet only through the metric source $M$ and the compact handoff $K$.

The finite coordinate window is opened next. The Kuratowski row $Q$ supplies distance-function observations, the finite epsilon-net row $F$ supplies the displayed center and coverage budget, and the Real row $R$ supplies the coordinate readbacks.

The structural rows then package exactly that handoff. Componentwise transport $H$ preserves the same finite route, replay $C$ exposes it to downstream consumers, provenance $P$ records the package lineage, and $N$ names the local certificate. Therefore the embedding consumer receives only the displayed finite coordinate handoff and not any hidden host embedding principle.
\end{proof}

\closureat{MengerNobelingEmbeddingUp}{seedStr}

\begin{closurestatus}{\MengerNobelingEmbeddingUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:menger-nobeling-embedding-carrier}, \autoref{thm:menger-nobeling-embedding-namecert-obligations}, and \autoref{thm:menger-nobeling-embedding-finite-coordinate-handoff} seed the finite coordinate embedding route over MetricUp, CompactMetricUp, KuratowskiEmbeddingUp, FiniteEpsilonNetUp, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, host Euclidean embedding, selected infinite coordinate families, quotient completion, open-cover compactness, countable choice, ambient dimension principles, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net exposure, Kuratowski coordinate handoff, finite separation stability, Real readback, transport, replay, provenance, and local naming for BEDC.Derived.MengerNobelingEmbeddingUp.}
  \constructivestory{A $\MengerNobelingEmbeddingUp$ packet is generated from a MetricUp source row, a CompactMetricUp handoff, a KuratowskiEmbeddingUp distance-function row, a FiniteEpsilonNetUp coordinate budget, a RealUp readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
