\chapter{A Concrete Naming Certificate for $\CauchyFilterRegularizationUp$}
\label{ch:concrete-instances-cauchy-filter-regularization-namecert}
\origin{human}

Following Kelley and Bishop--Bridges, the $\CauchyFilterRegularizationUp$ packet records the L10 handoff that turns a displayed Cauchy-filter completion route into a regular Cauchy real-name route through finite BEDC rows. It sits after the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the completion boundary of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}, the Polish carrier discipline of \autoref{ch:concrete-instances-polishspace-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only the finite regularization handoff; it does not quotient filters, select representatives, import countable choice, assert host equality of limits, or use ambient $\RealUp$ completeness.

\begin{definition}[Cauchy-filter regularization carrier]
\label{def:cauchy-filter-regularization-carrier}
A $\CauchyFilterRegularizationUp$ carrier is a finite $\BHist$ packet
$$
G=(F,W,D,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the source $\CauchyFilterUp/\CauchyFilterCompletionUp$ row, naming the finite filter observations and the completion-facing boundary they expose.
\item $W$ is the $\StreamNameUp$ window schedule opened for regularization requests and tail comparisons.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the same windows, comparison radii, and completion requests.
\item $R$ is the $\RegSeqRatUp$ readback row produced from the displayed windows and dyadic tolerance data.
\item $L$ is the terminal $\RealUp$ seal row reached only after $F,W,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the filter-completion source, stream windows, dyadic ledger, regular readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a regularization request through $F,W,D,R,L,H,P,N$.
\item $P$ records $\Pkg$ provenance over $\CauchyFilterRegularizationUp$, $\CauchyFilterUp$, $\CauchyFilterCompletionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyFilterRegularizationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,W,D,R,L,H,C,P,N$. It stores no quotient filter, selected completion point, hidden cofinal subsequence, host real equality, countable-choice schedule, or ambient completeness coordinate.
\end{definition}

\begin{theorem}[Cauchy-filter regularization NameCert obligations]
\label{thm:cauchy-filter-regularization-namecert-obligations}
For every accepted $\CauchyFilterRegularizationUp$ carrier
$$
G=(F,W,D,R,L,H,C,P,N),
$$
the local $\NameCert_{\CauchyFilterRegularizationUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed source, window, tolerance, readback, seal, transport, replay, provenance, and local-name rows;
\item filter exposure, requiring every regularization read to expose the $\CauchyFilterUp/\CauchyFilterCompletionUp$ row $F$ before a stream window is inspected;
\item window and tolerance exactness, requiring the $\StreamNameUp$ row $W$ and $\DyadicRatCoreUp$ row $D$ to determine every finite comparison used by the handoff;
\item $\RegSeqRatUp$ handoff, requiring the regular rational row $R$ to be read from the displayed $W,D$ data and not from a hidden representative;
\item $\RealUp$-seal nonescape, requiring the terminal row $L$ to be consumed only after $F,W,D,R$ have been displayed;
\item provenance, requiring $H,C,P,N$ to transport, replay, source, and name the same finite packet without adding quotient filters, selected limits, choice, host equality, or ambient completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-filter-regularization-carrier}. The source row $F$ exposes the Cauchy-filter completion boundary, and the rows $W,D,R,L$ are the only non-structural regularization rows downstream from that boundary.

The window and tolerance part is finite. A regularization request opens the listed $\StreamNameUp$ windows in $W$, reads the dyadic tolerance budget in $D$, and then obtains the $\RegSeqRatUp$ row $R$ from those displayed observations.

The real-seal handoff is last. The terminal row $L$ is reachable only after $F,W,D,R$ have been exposed, while $H,C,P,N$ only transport, replay, source, and name the same packet. Since no remaining coordinate stores quotient filters, selected representatives, hidden cofinal choices, host real equality, or ambient completeness, the listed clauses exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{Every accepted $\CauchyFilterRegularizationUp$ consumer that reaches a $\RealUp$ seal without reading the displayed CauchyFilter and CauchyFilterCompletion source, StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat handoff, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert row refutes the packet surface.}

\independenceWitness{cauchyfiltercompletion, polishspace, streamname, dyadicratcore, regseqrat, real: $\CauchyFilterRegularizationUp$ is not bijective to any listed sibling because it binds a Cauchy-filter completion boundary, finite window schedule, dyadic tolerance ledger, regular rational handoff, Real seal, transport, replay, provenance, and local naming into one L10 regularization certificate.}

\closureat{CauchyFilterRegularizationUp}{seedStr}

\begin{closurestatus}{\CauchyFilterRegularizationUp}
  \constructivestory{A $\CauchyFilterRegularizationUp$ packet is generated from a CauchyFilter/CauchyFilterCompletion source row, StreamName windows, a DyadicRatCore tolerance ledger, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-filter-regularization-carrier} and \autoref{thm:cauchy-filter-regularization-namecert-obligations} seed the L10 Cauchy-filter regularization handoff over CauchyFilterUp, CauchyFilterCompletionUp, StreamNameUp, DyadicRatCoreUp, RegSeqRatUp, RealUp, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filters, selected representatives, hidden cofinal choices, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove carrier admission, filter exposure, window exactness, tolerance exactness, RegSeqRat handoff, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CauchyFilterRegularizationUp.}
\end{closurestatus}
