\chapter{A Concrete Naming Certificate for $\StreamNameModulusUp$}
\label{ch:concrete-instances-streamname-modulus-namecert}
\origin{human}

Following Bishop and Bridges, a constructive modulus is treated as displayed
finite control on later observations rather than as a selected limit object.
The $\StreamNameModulusUp$ packet sits between the stream-name observation
surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic
readback rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the
regular rational consumer of \autoref{ch:concrete-instances-regseqrat-namecert},
and the real-seal boundary of \autoref{ch:concrete-instances-real-namecert}.
It records the finite witness by which a StreamName observation budget can be
handed to RegSeqRat and Real consumers without claiming a completed stream
quotient, a host-selected tail, or equality of real representatives.

\begin{definition}[Stream-name modulus carrier]
\label{def:streamname-modulus-carrier}
A $\StreamNameModulusUp$ carrier is a finite $\BHist$ packet
$$
U=(S,D,R,E,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ source row, containing the requested stream
name, observed positions, and local observation budget.
\item $D$ is the $\DyadicRatCoreUp$ readback row for the inspected positions.
\item $R$ is the $\RegSeqRatUp$ handoff row that receives the finite dyadic
windows and their regularity ledger.
\item $E$ is the $\RealUp$ seal-request row, recording only the downstream
consumer boundary that may later consume $R$.
\item $W$ is the modulus ledger: for each requested precision it displays a
finite stream position, the associated dyadic readback, and the regular-rational
handoff row visible at that position.
\item $H$ records componentwise $\hsame$ transport for $S,D,R,E,W$ and the
local certificate data.
\item $C$ records displayed $\Cont$ replay from a precision request to the
stream position, from that position to the dyadic readback, and from the
readback to the RegSeqRat handoff.
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\DyadicRatCoreUp$,
$\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StreamNameModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these nine rows. It has
no coordinate for a completed stream quotient, an ambient limit selector, a
host real equality proof, or a tail chosen outside the displayed observation
ledger.
\end{definition}

\begin{theorem}[Stream-name modulus pointwise stability]
\label{thm:streamname-modulus-pointwise-stability}
Let $U=(S,D,R,E,W,H,C,P,N)$ be an accepted $\StreamNameModulusUp$ carrier. If a
downstream consumer transports the displayed stream, dyadic readback, RegSeqRat
handoff, Real seal-request, and modulus ledger along the componentwise
$\hsame$ rows in $H$, then each precision request reads the same finite
position of $S$, the same dyadic row of $D$, and the same regular-rational
handoff in $R$ after replay through $C$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:streamname-modulus-carrier}. The only
precision-facing data are the rows $S,D,R,E,W$ together with transport,
replay, provenance, and the local name.

The modulus ledger $W$ binds each requested precision to one displayed stream
position and one displayed dyadic readback. Componentwise transport through
$H$ moves those rows together, so a transported request cannot alter the
position without also altering the visible ledger row.

Replay through $C$ reconstructs the same path from the precision request to
$S$, then to $D$, then to $R$. The rows $P$ and $N$ only source and name this
finite route; they do not add an external tail or equality proof.
\end{proof}

\begin{theorem}[Stream-name modulus RegSeqRat readiness]
\label{thm:streamname-modulus-regseqrat-readiness}
An accepted $\StreamNameModulusUp$ packet can be consumed by a
$\RegSeqRatUp$ row only as the finite route
$$
S,D,W \longmapsto R
$$
together with $H,C,P,N$. The handoff supplies displayed stream positions,
dyadic observations, and regularity ledger rows, but it does not supply a
completed sequence quotient, a selected tail, a host convergence theorem, or a
real-equality witness.
\end{theorem}
\begin{proof}
Begin with the carrier projection. The RegSeqRat row $R$ is not independent;
it is stored beside the stream source $S$, dyadic readback $D$, and modulus
ledger $W$.

Use pointwise stability from
\autoref{thm:streamname-modulus-pointwise-stability}. Every transported
precision request still reaches $R$ through the same visible stream position
and dyadic observation.

The RegSeqRat consumer therefore receives only the displayed finite route and
its support rows. Since the carrier has no coordinate for quotient sequences,
selected tails, host convergence, or real equality, none of those objects can
be exported at the RegSeqRat boundary.
\end{proof}

\begin{theorem}[Stream-name modulus Real handoff]
\label{thm:streamname-modulus-real-handoff}
A $\RealUp$ consumer of an accepted $\StreamNameModulusUp$ packet may import
only the RegSeqRat-facing handoff $R$, the Real seal-request row $E$, and the
finite stream/dyadic modulus route $S,D,W,H,C,P,N$. The packet therefore
prepares a RealUp handoff by finite observed windows and regular rational
rows, without asserting completeness of $\RealUp$, equality of Real
representatives, or convergence outside the carried ledger.
\end{theorem}
\begin{proof}
Apply \autoref{thm:streamname-modulus-regseqrat-readiness}. It identifies
$R$ as the only regular-rational object exported by the packet and forces the
route through $S,D,W,H,C,P,N$.

The Real-facing row $E$ records only that this regular-rational handoff is the
object a Real consumer may later inspect. It is a seal-request row, not a proof
of Real completeness or equality.

Thus the Real consumer receives the same finite modulus route that the
RegSeqRat consumer receives, together with the request row $E$. No ambient
limit, quotient equality, or external convergence datum is available.
\end{proof}

\begin{theorem}[Stream-name modulus NameCert obligations]
\label{thm:streamname-modulus-namecert-obligations}
For every accepted $\StreamNameModulusUp$ carrier
$U=(S,D,R,E,W,H,C,P,N)$, the local $\NameCert_{\StreamNameModulusUp}$ surface
consists exactly of carrier admission, stream-position exposure, dyadic
readback, RegSeqRat handoff, Real seal-request boundary, modulus-ledger
exactness, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$
provenance, and local naming. Every obligation is discharged inside the
displayed finite route and no obligation is stored outside $U$.
\end{theorem}
\begin{proof}
Carrier admission is the projection of the finite tuple in
\autoref{def:streamname-modulus-carrier}. The rows $S,D,R,E,W$ expose the
stream source, dyadic readback, regular-rational handoff, Real request, and
modulus ledger.

Pointwise stability supplies the transport obligation. Theorem~\ref{thm:streamname-modulus-pointwise-stability}
keeps precision requests attached to the same displayed stream and dyadic
rows under $\hsame$ movement.

The RegSeqRat readiness and Real handoff theorems supply the consumer-facing
obligations. They show that $R$ and $E$ can be read only through the carried
finite route.

Finally $C,P,N$ replay, source, and name the packet. Since no remaining carrier
coordinate exists, the listed obligations exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{An accepted $\StreamNameModulusUp$ consumer that reads
a $\RegSeqRatUp$ or $\RealUp$ handoff without first exposing the displayed
$\StreamNameUp$ positions, $\DyadicRatCoreUp$ readbacks, modulus ledger,
componentwise $\hsame$ rows, $\Cont$ replay, $\Pkg$ provenance, and local
$\NameCert$ row refutes the packet surface.}

\independenceWitness{streamname, dyadicratcore, regseqrat, real: none of the
listed sibling chapters supplies the whole modulus handoff
$U=(S,D,R,E,W,H,C,P,N)$, because each sibling contributes only the source
stream, dyadic readback, regular rational consumer, or Real seal boundary while
this chapter binds them into one finite modulus route.}

\closureat{StreamNameModulusUp}{seedStr}

\begin{closurestatus}{\StreamNameModulusUp}
  \constructivestory{A $\StreamNameModulusUp$ packet is generated from a $\StreamNameUp$ source row, $\DyadicRatCoreUp$ readbacks, a $\RegSeqRatUp$ handoff, a $\RealUp$ seal-request row, a modulus ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ data.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:streamname-modulus-carrier}, \autoref{thm:streamname-modulus-pointwise-stability}, \autoref{thm:streamname-modulus-regseqrat-readiness}, \autoref{thm:streamname-modulus-real-handoff}, and \autoref{thm:streamname-modulus-namecert-obligations} seed the finite modulus handoff from $\StreamNameUp$ observations to $\RegSeqRatUp$ and $\RealUp$ consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a completed stream quotient, selected tails, host convergence, Real equality, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove the finite modulus ledger, RegSeqRat readiness, and Real handoff obligations for BEDC.Derived.StreamNameModulusUp.}
\end{closurestatus}
