\chapter{A Concrete Naming Certificate for $\HeineBorelLocatedIntervalUp$}
\label{ch:concrete-instances-heine-borel-located-interval-namecert}
\origin{human}

Following Bishop and Bridges on compact intervals and located real-number approximation, the $\HeineBorelLocatedIntervalUp$ packet records the finite dyadic-net data available for a located closed interval. It sits over the real-name endpoint seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the closed bounded interval carrier of \autoref{ch:concrete-instances-closedboundedinterval-namecert}, and the compact-metric finite-net consumer of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet names the constructive finite-net substitute for interval compactness; it does not assert unrestricted open-cover compactness or a general Heine--Borel theorem for arbitrary subsets of $\RealUp$.

\begin{definition}[Heine--Borel located interval carrier]
\label{def:heine-borel-located-interval-carrier}
A $\HeineBorelLocatedIntervalUp$ carrier is a finite $\BHist$ packet
$$
L=(I,E,R,S,D,F,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\ClosedBoundedIntervalUp$ source row, exposing lower and upper endpoint names, interval membership, and boundedness witnesses.
\item $E$ is the $\RealUp$ endpoint seal row, read only through the finite endpoint windows attached to $I$.
\item $R$ is the $\RegSeqRatUp$ tolerance row naming the requested positive approximation scale and its finite readback.
\item $S$ is the $\StreamNameUp$ window row listing the inspected endpoint and mesh windows before any coverage handoff.
\item $D$ is the $\DyadicRatCoreUp$ subdivision ledger, recording the dyadic mesh, endpoint-radius comparisons, and inclusion checks for every displayed cell.
\item $F$ is the finite-net row, consisting of finitely many dyadic centers, their radius budget, and the cell-coverage witnesses obtained from $I,E,R,S,D$.
\item $K$ is the $\CompactMetricUp$ handoff row read after the finite-net row has been displayed.
\item $H$ records componentwise $\hsame$ transport for the interval, endpoint seal, tolerance, window, dyadic, finite-net, compact-metric handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from interval endpoint inspection through dyadic subdivision, finite-net coverage, compact-metric handoff, and local naming.
\item $P$ is the $\Pkg$ provenance over $\HeineBorelLocatedIntervalUp$, $\ClosedBoundedIntervalUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\CompactMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HeineBorelLocatedIntervalUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,E,R,S,D,F,K,H,C,P,N$. It has no coordinate for arbitrary open covers, selected subcover functionals, quotient real equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Heine--Borel located interval finite-net obligation]
\label{thm:heine-borel-located-interval-net-obligation}
For every accepted $\HeineBorelLocatedIntervalUp$ carrier $L=(I,E,R,S,D,F,K,H,C,P,N)$, the finite-net obligation is exactly the route
$$
I,E,R,S,D
\longmapsto
F
\longmapsto
K,H,C,P,N .
$$
Thus a compactness-facing consumer may read only the displayed closed bounded interval source, endpoint seals, regular rational tolerance, finite stream windows, dyadic subdivision ledger, finite dyadic centers, compact-metric handoff, transport, replay, provenance, and local NameCert rows. No read exports unrestricted open-cover compactness, a selected finite subcover outside $F$, quotient equality of real names, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:heine-borel-located-interval-carrier}. The interval source, endpoint seal, tolerance row, finite windows, and dyadic ledger are the only rows from which a net can be constructed.

The finite-net row $F$ is read after those rows. Its centers and radius budget are displayed dyadic data, and each coverage witness is tied to the same endpoint, tolerance, stream-window, and dyadic comparison surface.

Finally $K,H,C,P,N$ hand the displayed net to compact-metric consumers while preserving transport, replay, provenance, and local naming. Since no carrier coordinate stores arbitrary open covers, selected subcovers, quotient real equality, countable choice, or ambient completeness, the local obligation surface exports none of those data.
\end{proof}

\begin{theorem}[Heine--Borel located interval compact-metric handoff]
\label{thm:heine-borel-located-interval-compact-metric-handoff}
Every $\CompactMetricUp$ consumer of an accepted $\HeineBorelLocatedIntervalUp$ packet must first display the finite dyadic-net row $F$ together with its source rows $I,E,R,S,D$ and structural rows $H,C,P,N$. The handoff is a finite located closed-interval coverage certificate over $\ClosedBoundedIntervalUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$; it is not an open-cover compactness theorem, a selected subcover principle, a quotient-completion statement, or an ambient completeness assertion.
\end{theorem}
\begin{proof}
Start from the finite-net obligation of \autoref{thm:heine-borel-located-interval-net-obligation}. It forces the compact-metric consumer to read the interval, endpoint, tolerance, window, dyadic, and finite-net rows before $K$ is available.

Read the compact-metric handoff row $K$ next. This row packages only the displayed centers, mesh radius, and cell-coverage witnesses already stored in $F$; it does not add a host compactness theorem or a cover selector.

The transport and replay rows $H,C$ keep the same finite dyadic data stable under accepted componentwise reads, while $P,N$ bind provenance and local naming. Hence the handoff remains a finite located interval certificate and cannot export open-cover compactness, selected subcovers, quotient completion, or ambient completeness.
\end{proof}

\falsifiablePrediction{A compact-metric consumer that reads $\HeineBorelLocatedIntervalUp$ without displaying the closed bounded interval, Real endpoint seals, regular rational tolerance, stream windows, DyadicRatCore subdivision ledger, finite dyadic net, compact-metric handoff, transport, replay, provenance, and local NameCert rows refutes the carrier surface.}

\independenceWitness{closedboundedinterval, real, regseqrat, streamname, dyadicratcore, compactmetric: no listed sibling is bijective to $\HeineBorelLocatedIntervalUp$ because this packet binds located closed-interval endpoints, tolerance readback, finite windows, dyadic subdivision, finite-net coverage, compact-metric handoff, transport, replay, provenance, and local naming in one interval-coverage interface.}

\closureat{HeineBorelLocatedIntervalUp}{seedStr}

\begin{closurestatus}{\HeineBorelLocatedIntervalUp}
  \constructivestory{A $\HeineBorelLocatedIntervalUp$ packet is generated from a ClosedBoundedIntervalUp source row, RealUp endpoint seals, a RegSeqRatUp tolerance row, StreamNameUp finite windows, a DyadicRatCoreUp subdivision ledger, a finite dyadic-net row, a CompactMetricUp handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:heine-borel-located-interval-carrier}, \autoref{thm:heine-borel-located-interval-net-obligation}, and \autoref{thm:heine-borel-located-interval-compact-metric-handoff} seed the finite located closed-interval net interface for compact-metric consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim unrestricted open-cover compactness, general Heine--Borel compactness for subsets of $\RealUp$, selected subcovers, quotient real equality, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, endpoint sealing, tolerance readback, finite-window replay, dyadic subdivision, finite-net coverage, compact-metric handoff, transport, provenance, and local naming for BEDC.Derived.HeineBorelLocatedIntervalUp.}
\end{closurestatus}
