\chapter{A Concrete Naming Certificate for $\MinimalTriggerLiftBundleUp$}
\label{ch:concrete-instances-minimal-trigger-lift-bundle-namecert}
\origin{ai}

The $\MinimalTriggerLiftBundleUp$ packet realizes the lift-fiber decomposition of \autoref{thm:philosophy-minimal-trigger-lift-bundle-decomposition} as finite BEDC NameCert data. It sits beside the codon-window carrier of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the lift-orbit classifier of \autoref{ch:concrete-instances-codon-lift-orbit-classifier-namecert}, the DNA boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, and the trigger-algebra surface of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}. The packet records quotient supports, binary lift choices, orbit fibers, and lift-flip ledgers as displayed finite rows; it is not biological mechanism, stochastic fitness, host quotient semantics, or an unrecorded enumeration oracle.

\begin{definition}[Minimal trigger lift-bundle carrier]
\label{def:minimal-trigger-lift-bundle-carrier}
A $\MinimalTriggerLiftBundleUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,L,O,F,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the quotient-support row, listing a quotient-level minimal trigger and its displayed support cells.
\item $L$ is the lift-choice row, recording one binary $f_{3}$ lift coordinate for each displayed quotient support.
\item $O$ is the orbit-fiber row, naming the fiber dimension and orbit type read from the quotient minimal-trigger table.
\item $F$ is the finite fiber-count row, displaying the $Q_{1}$, $Q_{2}$, $Q_{3}$, and $Q_{4}$ multiplicities and the codon count readback.
\item $G$ is the lift-flip ledger, recording the within-fiber one-coordinate flip graph and its edge-count row.
\item $H$ records componentwise $\hsame$ transport for quotient supports, lift choices, orbit fibers, fiber counts, lift-flip ledgers, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from a quotient support through lift choices, fiber counting, orbit labeling, and flip-ledger exposure.
\item $P$ is the $\Pkg$ provenance over $\MinimalTriggerLiftBundleUp$, the source theorem \autoref{thm:philosophy-minimal-trigger-lift-bundle-decomposition}, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\MinimalTriggerLiftBundleUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,L,O,F,G,H,C,P,N$. It has no coordinate for hidden quotient semantics, empirical biology, probabilistic fitness, an unrestricted search space, or a lift choice detached from the displayed quotient support.
\end{definition}

\begin{theorem}[Minimal trigger lift-bundle NameCert obligations]
\label{thm:minimal-trigger-lift-bundle-namecert-obligations}
For every accepted $\MinimalTriggerLiftBundleUp$ carrier $B=(Q,L,O,F,G,H,C,P,N)$, the local $\NameCert_{\MinimalTriggerLiftBundleUp}$ surface consists exactly of quotient-support admission through $Q$, lift-choice admission through $L$, orbit-fiber readback through $O$, finite fiber-count preservation through $F$, lift-flip ledger exposure through $G$, componentwise $\hsame$ transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$. The carrier admits no read of a codon-level trigger before the quotient support and the matching lift-choice row have both been displayed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:minimal-trigger-lift-bundle-carrier}. The quotient-support row $Q$ fixes the base trigger, and the lift-choice row $L$ records exactly one binary lift coordinate for each displayed support.

The orbit-fiber row $O$ and count row $F$ are read from the decomposition of \autoref{thm:philosophy-minimal-trigger-lift-bundle-decomposition}. The lift-flip row $G$ records adjacency only inside the same displayed fiber, so no cross-fiber bijection is introduced.

Transport and replay preserve the rows componentwise, while provenance and local naming source the same finite packet. Therefore the listed rows exhaust the local NameCert obligations and prevent detached quotient semantics or hidden enumeration data.
\end{proof}

\begin{theorem}[Minimal trigger lift-bundle vision handoff]
\label{thm:minimal-trigger-lift-bundle-vision-handoff}
The decomposition
$$
\mathcal{T}_{c}=Q_{1}\sqcup25Q_{2}\sqcup22Q_{3}\sqcup Q_{4}
$$
is consumed by $\MinimalTriggerLiftBundleUp$ only through the finite route
$$
Q,L \longmapsto O,F,G \longmapsto H,C,P,N .
$$
Later Lean-facing TasteGate files for this packet must provide $\mathsf{Nontrivial}\ \MinimalTriggerLiftBundleUp$ and $\mathsf{FieldFaithful}\ \MinimalTriggerLiftBundleUp$ instances before the packet can serve as a verified downstream trigger-lattice consumer.
\end{theorem}
\begin{proof}
Read the source decomposition through its displayed finite rows. The quotient support gives $Q$, and the independent binary lift choices give $L$.

The fiber dimension, multiplicity, and codon count are then recorded by $O$ and $F$. The lift-flip graph row $G$ is internal to each fiber and does not identify different quotient supports.

The structural rows $H,C,P,N$ transport, replay, source, and name exactly that finite route. The stated TasteGate obligations are therefore downstream instance requirements, not hidden assumptions inside the present paper carrier.
\end{proof}

\falsifiablePrediction{For every accepted $\MinimalTriggerLiftBundleUp$ packet, replacing each displayed row by a componentwise $\hsame$ row preserves the finite fiber counts $1,25,22,1$ over $Q_{1},Q_{2},Q_{3},Q_{4}$ and the codon total $294$.}

\independenceWitness{codon-six-bit-window, codon-lift-orbit-classifier, dna-window-six-boundary-tile, window-coverage-trigger-algebra: none is bijective with $\MinimalTriggerLiftBundleUp$ because this packet jointly carries quotient supports, lift-choice vectors, orbit fibers, finite fiber counts, lift-flip ledgers, componentwise transport, replay, provenance, and local naming.}

\closureat{MinimalTriggerLiftBundleUp}{seedStr}

\begin{closurestatus}{\MinimalTriggerLiftBundleUp}
  \constructivestory{A $\MinimalTriggerLiftBundleUp$ packet is generated from quotient-support rows, binary lift-choice rows, orbit-fiber rows, finite fiber-count rows, lift-flip ledgers, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:minimal-trigger-lift-bundle-carrier}, \autoref{thm:minimal-trigger-lift-bundle-namecert-obligations}, and \autoref{thm:minimal-trigger-lift-bundle-vision-handoff} seed the finite lift-fiber NameCert route over quotient supports, lift choices, orbit fibers, fiber counts, and flip ledgers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological mechanism, stochastic fitness, host quotient semantics, unrestricted trigger search, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked quotient-support admission, lift-choice admission, orbit-fiber readback, finite fiber-count preservation, lift-flip ledger exposure, and TasteGate instances for BEDC.Derived.MinimalTriggerLiftBundleUp.}
\end{closurestatus}
