\chapter{A Concrete Naming Certificate for $\LocatedCompletionUp$}
\label{ch:concrete-instances-located-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedCompletionUp$ packet records the finite located completion surface used by the L10 Real and Completion route. It sits between the located metric source of \autoref{ch:concrete-instances-locatedmetric-namecert}, the separated completion boundary of \autoref{ch:concrete-instances-separatedcompletion-namecert}, the dense completion entry of \autoref{ch:concrete-instances-completionembedding-namecert}, and the located completion space interface of \autoref{ch:concrete-instances-located-completion-space-namecert}. The packet is a displayed NameCert route for located completion data; it is not a quotient completion, a selected representative, a countable-choice schedule, host equality of completed points, or ambient $\RealUp$ completeness.

\begin{definition}[LocatedCompletion carrier]
\label{def:located-completion-carrier}
A $\LocatedCompletionUp$ carrier is a finite $\BHist$ packet
$$
L=(M,S,E,W,R,D,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\LocatedMetricUp$ source row, including the metric carrier, located distance comparison, and finite request discipline consumed before completion data are public.
\item $S$ is the $\SeparatedCompletionUp$ boundary row, read before completed names may be compared as separated.
\item $E$ is the $\CompletionEmbeddingUp$ row by which source observations enter the completion-facing route.
\item $W$ is the $\StreamNameUp$ finite-window row exposed before any regular rational readback.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the displayed stream windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling located comparison, Cauchy tail requests, and zero-distance checks.
\item $A$ is the terminal $\RealUp$ seal reached only after $M,S,E,W,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the located metric source, separated boundary, embedding, window, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion request through the same ordered rows.
\item $P$ is the $\Pkg$ provenance over $\LocatedCompletionUp$, $\LocatedMetricUp$, $\SeparatedCompletionUp$, $\CompletionEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $M,S,E,W,R,D,A,H,C,P,N$. It has no coordinate for quotient completion equality, selected completed representatives, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[LocatedCompletion NameCert obligations]
\label{thm:located-completion-namecert-obligations}
For every accepted $\LocatedCompletionUp$ carrier $L=(M,S,E,W,R,D,A,H,C,P,N)$, the local $\NameCert_{\LocatedCompletionUp}$ surface consists exactly of carrier admission, located metric source exposure, separated completion exposure, dense embedding coverage, finite stream-window exactness, regular rational readback, dyadic tolerance accounting, terminal Real sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every Real or completion-facing consumer must read those rows in the displayed route before it can use the local name.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-completion-carrier}. The displayed analytic rows are the located metric source $M$, separated completion boundary $S$, completion embedding $E$, stream windows $W$, regular readback $R$, dyadic tolerance ledger $D$, and Real seal $A$.

Read the source and embedding side first. The $\LocatedMetricUp$ row supplies located distance data, the $\CompletionEmbeddingUp$ row admits source observations, and the $\SeparatedCompletionUp$ row supplies the separated comparison boundary named in \autoref{ch:concrete-instances-separatedcompletion-namecert}.

The numerical route is finite. The stream windows $W$ and dyadic ledger $D$ precede the $\RegSeqRatUp$ readback $R$, and $R$ precedes the terminal $\RealUp$ seal $A$.

Finally attach $H,C,P,N$. These rows transport, replay, source, and name the same route, while the carrier lists no quotient completion, selected representative, host equality, choice schedule, or ambient completeness coordinate. Hence the listed rows exhaust the local $\NameCert_{\LocatedCompletionUp}$ obligations.
\end{proof}

\begin{theorem}[LocatedCompletion L10 handoff]
\label{thm:located-completion-l10-handoff}
Every $\LocatedCompletionUp$ consumer route factors through the finite L10 chain
$$
\LocatedMetricUp \longmapsto \CompletionEmbeddingUp \longmapsto \SeparatedCompletionUp \longmapsto \StreamNameUp,\DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The handoff is the same route consumed by the located completion space chapter of \autoref{ch:concrete-instances-located-completion-space-namecert}; it exports no quotient completion, selected completed point, host equality, countable-choice selector, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Use \autoref{thm:located-completion-namecert-obligations} to expose the full packet route. The located metric row, dense embedding, separated boundary, finite windows, tolerance ledger, readback, and Real seal must all be displayed before the local name is available.

Compare this route with \autoref{ch:concrete-instances-located-completion-space-namecert}. The located completion space interface consumes the same sibling rows but packages them as a space-facing boundary, while the present chapter packages them as the local located completion object.

No additional completion principle remains. The structural rows $H,C,P,N$ merely transport, replay, source, and name the displayed chain, and the refused quotient, selection, equality, choice, and ambient-completeness objects have no coordinate in the carrier.
\end{proof}

\falsifiablePrediction{Every accepted $\LocatedCompletionUp$ consumer displays a $\LocatedMetricUp$ source row, a $\CompletionEmbeddingUp$ dense entry row, a $\SeparatedCompletionUp$ boundary row, $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ tolerance ledger, a $\RegSeqRatUp$ readback row, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}

\independenceWitness{locatedmetric, separatedcompletion, completionembedding, streamname, regseqrat, dyadicratcore, real: $\LocatedCompletionUp$ is not bijective to any listed sibling because it jointly carries located metric source data, dense entry, separated completion boundary, finite stream windows, dyadic tolerance, regular readback, Real sealing, transport, continuation, provenance, and local naming as one completion packet.}

\closureat{LocatedCompletionUp}{seedStr}

\begin{closurestatus}{\LocatedCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-completion-carrier}, \autoref{thm:located-completion-namecert-obligations}, and \autoref{thm:located-completion-l10-handoff} seed the finite located completion surface over $\LocatedMetricUp$, $\SeparatedCompletionUp$, $\CompletionEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected completed representatives, host equality of completed points, countable choice, Lean verification, bridge checking, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, located source exposure, separated completion compatibility, embedding coverage, finite readback exactness, Real seal exactness, transport replay, and non-escape over the same displayed packet.}
  \constructivestory{A $\LocatedCompletionUp$ packet is generated from a located metric source, a dense completion entry, a separated completion boundary, finite stream windows, dyadic tolerances, regular rational readback, a Real seal, and structural NameCert rows.}
\end{closurestatus}
