\chapter{A Concrete Naming Certificate for $\BrouwerMonotoneSequenceUp$}
\label{ch:concrete-instances-brouwer-monotone-sequence-namecert}
\origin{human}

Following Brouwer and Bishop--Bridges on monotone sequences in constructive analysis, the $\BrouwerMonotoneSequenceUp$ packet records a monotone real-name boundary object through finite stream windows, regular rational readback, dyadic tolerance ledgers, and the terminal real-name seal. It sits after the Specker obstruction of \autoref{ch:concrete-instances-speckersequence-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the Real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter gives the L10 Real and Completion frontier a named monotone-sequence carrier without claiming located suprema, trichotomy, countable choice, selected limits, quotient stream representatives, or ambient $\RealUp$ completeness.

\begin{definition}[BrouwerMonotoneSequence carrier]
\label{def:brouwer-monotone-sequence-carrier}
A $\BrouwerMonotoneSequenceUp$ carrier is a finite $\BHist$ packet
$$
B=(S,W,D,R,E,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source-sequence row, listing the inspected indices and their finite dependency order.
\item $W$ is the finite family of $\StreamNameUp$ windows opened for the inspected real-name entries.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the displayed windows and monotonicity comparisons.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the windows and dyadic tolerance ledger.
\item $E$ is the terminal $\RealUp$ seal row reached only after $S,W,D,R$ have been displayed.
\item $M$ is the monotonicity ledger, recording only finite adjacent-window comparison obligations among the displayed entries.
\item $H$ records componentwise $\hsame$ transport for source indices, windows, dyadic ledgers, readback, Real seals, monotonicity, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a monotone-sequence request through $S,W,D,R,E,M,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BrouwerMonotoneSequenceUp$, $\SpeckerSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BrouwerMonotoneSequenceUp}$ row.
\end{enumerate}
The classifier accepts only packets whose monotone-sequence request displays these rows in order. It has no coordinate for a located supremum, trichotomy decision, countable-choice selector, selected limit, quotient stream representative, or ambient $\RealUp$ completeness theorem.
\end{definition}

\begin{theorem}[BrouwerMonotoneSequence NameCert obligations]
\label{thm:brouwer-monotone-sequence-namecert-obligations}
For every accepted $\BrouwerMonotoneSequenceUp$ carrier
$$
B=(S,W,D,R,E,M,H,C,P,N),
$$
the local $\NameCert_{\BrouwerMonotoneSequenceUp}$ surface consists exactly of carrier admission for the inspected source sequence, finite stream windows, dyadic tolerance ledger, regular rational readback, Real seal, finite monotonicity ledger, componentwise transport, displayed replay, package provenance, and local naming rows. No NameCert obligation may be discharged by a located supremum, trichotomy of real names, countable-choice schedule, selected limit, quotient stream representative, or ambient complete real line.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:brouwer-monotone-sequence-carrier}. The analytic rows are precisely the source schedule $S$, the finite windows $W$, the dyadic tolerance ledger $D$, the regular rational readback $R$, the Real seal $E$, and the finite monotonicity ledger $M$.

The monotonicity information is local to the displayed windows. Each comparison read in $M$ consumes only the adjacent source entries already opened through $S,W,D,R$ and does not add a global order decision for arbitrary real names.

The structural rows add no hidden analytic principle. Transport through $H$ preserves the same displayed rows, replay through $C$ follows the same finite route, and $P,N$ record provenance and local naming for the packet.

Since the carrier has no row for located suprema, trichotomy, countable-choice schedules, selected limits, quotient stream representatives, or ambient completeness, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[BrouwerMonotoneSequence finite-window nonescape]
\label{thm:brouwer-monotone-sequence-finite-window-nonescape}
Every consumer read of an accepted $\BrouwerMonotoneSequenceUp$ carrier reaches a $\RealUp$ seal only through the finite route
$$
\StreamNameUp
\longmapsto
\DyadicRatCoreUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The route may consult the finite monotonicity ledger $M$ for displayed adjacent windows, but it cannot escape to a located supremum, countable-choice selector, trichotomy oracle, selected limit, quotient stream representative, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with a consumer read of the accepted carrier. The source row $S$ exposes only the inspected indices, so the first real-name data available to the consumer are the finite $\StreamNameUp$ windows in $W$.

The dyadic and regular-rational rows determine the only readback route. The tolerance ledger $D$ bounds the displayed windows, and the row $R$ packages those bounded observations as $\RegSeqRatUp$ readback data.

The terminal seal is downstream of those rows. The $\RealUp$ row $E$ is available only after $S,W,D,R$ have been displayed, and the monotonicity ledger $M$ can compare only the adjacent windows already present in the same finite packet.

Transport, replay, provenance, and local naming preserve this order through $H,C,P,N$. Therefore every consumer read remains inside the displayed finite-window route and cannot import a located supremum, trichotomy oracle, choice schedule, selected limit, quotient stream representative, or ambient completeness theorem.
\end{proof}

\closureat{BrouwerMonotoneSequenceUp}{seedStr}

\begin{closurestatus}{\BrouwerMonotoneSequenceUp}
  \constructivestory{A $\BrouwerMonotoneSequenceUp$ packet is generated from inspected source indices, finite StreamName windows, DyadicRatCore tolerance rows, RegSeqRat readback, a RealUp seal, a finite monotonicity ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:brouwer-monotone-sequence-carrier}, \autoref{thm:brouwer-monotone-sequence-namecert-obligations}, and \autoref{thm:brouwer-monotone-sequence-finite-window-nonescape} seed the constructive monotone-sequence boundary for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close located suprema, trichotomy, countable choice, selected limits, quotient stream representatives, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window monotonicity, StreamName exposure, DyadicRatCore tolerance accounting, RegSeqRat readback, RealUp seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BrouwerMonotoneSequenceUp.}
\end{closurestatus}
