\chapter{A Concrete Naming Certificate for $\ScottDomainUp$}
\label{ch:concrete-instances-scott-domain-namecert}
\origin{human}

Following Scott and Abramsky--Jung on domain theory, the $\ScottDomainUp$ packet records a finite naming certificate for the order-theoretic surface used by domain semantics before any completion-facing consumer reads a dcpo-style object. It sits after the preorder surface of \autoref{ch:concrete-instances-preorder-namecert}, the observable open-test discipline of \autoref{ch:concrete-instances-sierpinski-space-namecert}, the represented-space handoff of \autoref{ch:concrete-instances-representedspace-namecert}, and the finite stream window route of \autoref{ch:concrete-instances-streamname-namecert}. The packet names a displayed directed-supremum carrier; it does not assert a host dcpo, quotient domain, selected basis enumeration, classical lub principle, or ambient semantic completeness.

\begin{definition}[ScottDomain carrier]\label{def:scott-domain-carrier}
A $\ScottDomainUp$ carrier is a finite $\BHist$ packet
$$
D=(O,S,U,B,A,V,R,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $O$ is the preorder and partial-order carrier row, exposing the displayed comparison relation and the antisymmetry witness used by the local packet;
\item $S$ is the directed-family schedule row, listing the finite inspection schedule for the directed pieces that a consumer may request;
\item $U$ is the supremum row, recording the displayed least-upper-bound read served by the finite directed-family schedule;
\item $B$ is the compact-basis approximation row, listing the compact basis tokens and finite approximation evidence visible to the packet;
\item $A$ is the approximation-order row, routing basis-token comparisons back through $O$ and the directed schedule $S$;
\item $V$ is the Scott-open observable row, read through $\SierpinskiSpaceUp$ tests rather than host subsets;
\item $R$ is the represented-space handoff row, packaging the same observations through $\RepresentedSpaceUp$ and finite $\StreamNameUp$ windows;
\item $H$ records componentwise $\hsame$ transport for $O,S,U,B,A,V,R$;
\item $C$ records displayed $\Cont$ replay of directed-supremum and Scott-open reads;
\item $P$ is the $\Pkg$ provenance over $\ScottDomainUp$, $\PreorderUp$, $\SierpinskiSpaceUp$, $\RepresentedSpaceUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ScottDomainUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host dcpo, quotient order, selected infinite basis enumeration, classical pointwise lub, ambient topology, or semantic completeness theorem.
\end{definition}

\begin{theorem}[ScottDomain NameCert obligations]\label{thm:scott-domain-namecert-obligations}
For the carrier of \autoref{def:scott-domain-carrier}, the local $\NameCert_{\ScottDomainUp}$ surface consists exactly of preorder and partial-order admission, directed-family schedule admission, supremum-row admission, compact-basis approximation admission, Scott-open observability, represented-space handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every consumer of the packet must read the rows $O,S,U,B,A,V,R,H,C,P,N$ before treating a directed supremum or Scott-open test as public.
\end{theorem}
\begin{proof}
Project the carrier. The order-theoretic rows are $O,S,U,B,A,V,R$, and the structural rows are $H,C,P,N$.

The preorder and partial-order read begins at $O$. A directed-supremum read then uses $S$ to expose the inspected directed schedule before $U$ names the supremum row.

The basis read is separate but attached. The compact-basis row $B$ and approximation row $A$ route finite basis tokens back through $O$ and $S$, so a consumer cannot replace the displayed approximation surface by a host basis enumeration.

Finally, the Scott-open observable row $V$ and represented-space row $R$ package those finite reads through \autoref{ch:concrete-instances-sierpinski-space-namecert}, \autoref{ch:concrete-instances-representedspace-namecert}, and \autoref{ch:concrete-instances-streamname-namecert}. Rows $H,C,P,N$ preserve, replay, source, and name the same carrier, exhausting the local obligations.
\end{proof}

\begin{theorem}[ScottDomain directed-supremum stability]\label{thm:scott-domain-directed-supremum-stability}
Every accepted $\ScottDomainUp$ packet preserves directed-supremum visibility under componentwise transport and continuation replay. If a consumer reads the supremum row $U$ through the directed-family schedule $S$, any transported or replayed read of the same packet factors again through
$$
O,S,U,B,A,V,R,H,C,P,N .
$$
Thus Scott-open observations and represented-space handoffs remain downstream of the displayed directed schedule and never expose a host dcpo, quotient domain, selected infinite basis enumeration, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with a directed-supremum read. By \autoref{def:scott-domain-carrier}, the read reaches $U$ only after the order row $O$ and the directed-family schedule $S$ are displayed.

Apply the NameCert obligations of \autoref{thm:scott-domain-namecert-obligations}. Componentwise transport through $H$ preserves the same rows, and $\Cont$ replay through $C$ reuses the displayed schedule rather than generating a second supremum source.

The observable and representation rows are downstream. A Scott-open test reads $V$ through the Sierpinski surface, and the represented-space handoff reads $R$ through finite stream windows. Since the excluded host objects are absent from $O,S,U,B,A,V,R,H,C,P,N$, no transported or replayed directed-supremum read can expose them.
\end{proof}

\closureat{ScottDomainUp}{seedStr}

\begin{closurestatus}{\ScottDomainUp}
  \constructivestory{A $\ScottDomainUp$ packet is generated from preorder and partial-order rows, directed-family schedules, supremum rows, compact-basis approximation rows, Scott-open observable rows, represented-space handoff rows, componentwise transport, continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:scott-domain-carrier}, \autoref{thm:scott-domain-namecert-obligations}, and \autoref{thm:scott-domain-directed-supremum-stability} seed the finite directed-supremum and Scott-open observation surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host dcpos, quotient domains, selected basis enumerations, classical lub principles, ambient topology, semantic completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean-backed carrier admission, directed-schedule stability, Scott-open observability, represented-space handoff, and local NameCert registration for BEDC.Derived.ScottDomainUp.}
\end{closurestatus}
