\chapter{A Concrete Naming Certificate for $\MetricCompletionKleisliUp$}
\label{ch:concrete-instances-metric-completion-kleisli-namecert}
\origin{human}

Following Mac Lane's Kleisli categories, and Bishop--Bridges and Kelley on metric completion, the $\MetricCompletionKleisliUp$ packet records the metric-specific bind consumer for completion-valued maps as finite BEDC data. It reads the metric completion carrier of \autoref{ch:concrete-instances-metriccompletion-namecert}, the metric adjunction route of \autoref{ch:concrete-instances-metric-completion-adjunction-namecert}, the Cauchy Kleisli consumer of \autoref{ch:concrete-instances-cauchy-completion-kleisli-namecert}, and the completion universal property of \autoref{ch:concrete-instances-completionuniversalproperty-namecert}. The chapter names a consumer route for bind-style completion reads; it is not a quotient completion, selected representative, countable-choice schedule, host equality of completed points, or ambient completeness theorem.

\begin{definition}[MetricCompletionKleisli carrier]
\label{def:metric-completion-kleisli-carrier}
A $\MetricCompletionKleisliUp$ carrier is a finite $\BHist$ packet
$$
K=(M,A,L,U,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricCompletionUp$ row, displaying the source metric, completion carrier, separated comparison, dense-source access, and readback branch before any bind consumer is opened.
\item $A$ is the $\MetricCompletionAdjunctionUp$ row, displaying the unit, counit, triangle ledger, and metric universal mapping boundary read by the consumer.
\item $L$ is the $\CauchyCompletionKleisliUp$ row, recording the unit, bind, and reassociated-bind consumer route inherited from the L10 completion algebra.
\item $U$ is the $\CompletionUniversalPropertyUp$ row, exposing the extension surface through which a displayed metric source map is consumed as a completion-valued map.
\item $R$ is the $\RegSeqRatUp$ readback row used by the metric completion and Cauchy Kleisli routes.
\item $E$ is the public $\RealUp$ seal row reached only after $M,A,L,U,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the metric completion row, metric adjunction row, Cauchy Kleisli row, universal-property row, regular readback, Real seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from a bind consumer request through $M,A,L,U,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MetricCompletionKleisliUp$, $\MetricCompletionUp$, $\MetricCompletionAdjunctionUp$, $\CauchyCompletionKleisliUp$, $\CompletionUniversalPropertyUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricCompletionKleisliUp}$ row.
\end{enumerate}
The classifier accepts only packets whose bind consumer first displays the metric completion, metric adjunction, Cauchy Kleisli, universal-property, regular readback, Real seal, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows listed above.
\end{definition}

\begin{theorem}[MetricCompletionKleisli NameCert obligations]
\label{thm:metric-completion-kleisli-namecert-obligations}
For every accepted $\MetricCompletionKleisliUp$ carrier
$$
K=(M,A,L,U,R,E,H,C,P,N),
$$
the local $\NameCert_{\MetricCompletionKleisliUp}$ surface consists exactly of metric-completion admission, metric-adjunction admission, Cauchy-Kleisli bind exposure, completion-universal-property exposure, RegSeqRat readback, Real seal readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through the rows of $K$. No obligation may be discharged by a quotient completion, selected Cauchy representative, countable-choice selector, host equality of completed points, or ambient complete metric space.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-completion-kleisli-carrier}. Its analytic rows are precisely the metric completion row $M$, the metric adjunction row $A$, the Cauchy Kleisli row $L$, the universal-property row $U$, the regular readback row $R$, and the Real seal row $E$.

The metric rows determine the order of access. A bind consumer opens $M$ before it can read the adjunction data in $A$, and it opens $A$ before the Cauchy Kleisli consumer $L$ can hand off unit, bind, or reassociated-bind requests to the universal-property row $U$.

Transport and replay add no analytic coordinate. The rows $H$ and $C$ compare and replay only the displayed completion, adjunction, Kleisli, universal-property, readback, and seal data.

Finally $P$ and $N$ source and name the same finite packet. Since no listed row stores a quotient completion, selected representative, countable-choice selector, host equality, or ambient complete metric space, the displayed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[MetricCompletionKleisli bind handoff]
\label{thm:metric-completion-kleisli-bind-handoff}
Every bind-style consumer read of an accepted $\MetricCompletionKleisliUp$ carrier factors through the finite route
$$
\MetricCompletionUp
\longmapsto
\MetricCompletionAdjunctionUp
\longmapsto
\CauchyCompletionKleisliUp
\longmapsto
\CompletionUniversalPropertyUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp .
$$
The handoff reaches the displayed $\RealUp$ seal only through componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\MetricCompletionKleisliUp}$ row carried by the same packet.
\end{theorem}
\begin{proof}
Begin with the metric completion row $M$. It displays the source metric, completion carrier, separated comparison, dense-source access, and readback branch before a consumer can request completion-valued bind data.

Next read the adjunction row $A$. The unit, counit, triangle ledger, and metric universal mapping boundary are the only route by which the metric completion packet exposes extension data to a downstream consumer.

Attach the Cauchy Kleisli row $L$ and the universal-property row $U$. The row $L$ supplies the unit, bind, and reassociated-bind consumer surface, while $U$ records the extension route that consumes a displayed source map as a completion-valued map.

The readback and seal rows close the route. The row $R$ supplies the regular rational readback used by both completion and Kleisli sides, and $E$ is the only public Real seal. The structural rows $H,C,P,N$ transport, replay, source, and name this same route, so no quotient completion, selected representative, choice schedule, host equality, or ambient completeness theorem can enter the handoff.
\end{proof}

\closureat{MetricCompletionKleisliUp}{seedStr}

\begin{closurestatus}{\MetricCompletionKleisliUp}
  \constructivestory{A $\MetricCompletionKleisliUp$ packet is generated from metric completion, metric adjunction, Cauchy Kleisli, completion universal property, RegSeqRat readback, Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-completion-kleisli-carrier}, \autoref{thm:metric-completion-kleisli-namecert-obligations}, and \autoref{thm:metric-completion-kleisli-bind-handoff} seed the metric-specific Kleisli consumer route for bind-style completion reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host equality of completed points, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, metric-adjunction exposure, Cauchy-Kleisli exposure, universal-property exposure, RegSeqRat/Real seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.MetricCompletionKleisliUp.}
\end{closurestatus}
