\chapter{A Concrete Naming Certificate for $\PolishBasisUp$}
\label{ch:concrete-instances-polish-basis-namecert}
\origin{human}

Following Bourbaki and Kelley, a countable basis for a Polish presentation is treated here as a finite naming certificate over an already displayed complete separable metric route. The $\PolishBasisUp$ packet sits beside the Polish-space synthesis of \autoref{ch:concrete-instances-polishspace-namecert}, the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the dense schedule of \autoref{ch:concrete-instances-separablemetric-namecert}, the completion handoff of \autoref{ch:concrete-instances-completemetric-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}. It names basic-open data as countable finite rows, not as an ambient topology, an open-cover principle, or a choice-selected basis.

\begin{definition}[Polish-basis carrier]
\label{def:polish-basis-carrier}
A $\PolishBasisUp$ carrier is a finite $\BHist$ packet
$$
B=(M,D,K,S,R,I,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ source row supplying the point-history carrier, distance classifier, and metric $\NameCert$ used by basis balls.
\item $D$ is the $\SeparableMetricUp$ dense-schedule row whose named centers are inspected by finite stream positions.
\item $K$ is the $\CompleteMetricUp$ handoff row over the same metric carrier; it is recorded so Polish-space consumers can pass from basis windows to complete-separable metric reads.
\item $S$ is the $\StreamNameUp$ row enumerating the basis-center names and the finite Cauchy-window requests visible to consumers.
\item $R$ is the $\RegSeqRatUp$ row that reads rational radii, tolerance windows, and comparison bounds from the same finite stream positions.
\item $I$ is the basis-index window row. It stores the finite index interval, center-name handle, radius handle, and requested observation window for each basic-open read.
\item $F$ is the finite-intersection refinement row. It records the displayed refinement witness that sends two accepted basis windows to a third window contained in their metric intersection.
\item $H$ records componentwise $\hsame$ transport for $M,D,K,S,R,I,F$ and the local certificate rows.
\item $C$ records displayed $\Cont$ replay from a basis request through metric comparison, dense-center inspection, rational-radius readback, finite-intersection refinement, and complete-separable handoff.
\item $P$ is the $\Pkg$ provenance over $\PolishBasisUp$, $\PolishSpaceUp$, $\MetricSpaceUp$, $\SeparableMetricUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\PolishBasisUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only by transporting $M,D,K,S,R,I,F,H,C,P,N$ to the same metric and stream-readback surface. It has no coordinate for a host topology, arbitrary open covers, selected dense points, quotient completion equality, or ambient set membership.
\end{definition}

\begin{theorem}[Polish-basis NameCert obligations]
\label{thm:polish-basis-namecert-obligations}
For every accepted $\PolishBasisUp$ carrier
$$
B=(M,D,K,S,R,I,F,H,C,P,N),
$$
the local $\NameCert_{\PolishBasisUp}$ surface consists exactly of metric-source admission, separable dense-schedule admission, complete-metric handoff admission, stream-window exposure, regular-rational readback, basis-index windowing, finite-intersection refinement, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $M,D,K,S,R,I,F,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:polish-basis-carrier}. The rows $M,D,K,S,R,I,F,H,C,P,N$ are the whole countable-basis packet.

The metric row $M$ fixes the surface on which basis balls are read. The dense schedule $D$, stream row $S$, and regular rational row $R$ then expose center names and radius windows as finite observations.

The basis-index row $I$ records the inspected finite window, and the refinement row $F$ supplies the finite witness for binary intersections of displayed basic opens. The completion handoff $K$ remains attached to the same metric carrier for Polish-space consumers.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since no further coordinate is present, the NameCert surface exports no host topology, open-cover compactness, selected dense points, quotient completion equality, or ambient set membership.
\end{proof}

\begin{theorem}[Polish-basis complete-separable handoff]
\label{thm:polish-basis-complete-separable-handoff}
Every accepted $\PolishBasisUp$ read handed to a $\PolishSpaceUp$ or $\CompleteSeparableMetricUp$ consumer factors through the $\MetricSpaceUp$ row $M$, $\SeparableMetricUp$ dense schedule $D$, $\CompleteMetricUp$ handoff $K$, $\StreamNameUp$ finite windows $S$, $\RegSeqRatUp$ readback $R$, basis-index windows $I$, finite-intersection refinement $F$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and local $\NameCert$ row $N$.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $B=(M,D,K,S,R,I,F,H,C,P,N)$. A Polish-space consumer first reads the metric source $M$, then the dense schedule $D$ through stream windows $S$ and regular rational observations $R$.

The basis-index row $I$ identifies the finite window being consumed. When a consumer asks for closure under finite intersections, $F$ supplies the displayed refinement witness over the same metric surface.

The complete-metric handoff $K$ is then available over that metric source, while $H,C,P,N$ transport, replay, source, and name the route. Thus the handoff is finite and cannot pass through a host topology, an arbitrary open cover, quotient completion equality, or a selected dense subset.
\end{proof}

\closureat{PolishBasisUp}{seedStr}

\begin{closurestatus}{\PolishBasisUp}
  \constructivestory{A $\PolishBasisUp$ packet is generated from MetricSpace rows, SeparableMetric dense schedules, CompleteMetric handoffs, StreamName windows, RegSeqRat readbacks, basis-index windows, finite-intersection refinement rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:polish-basis-carrier}, \autoref{thm:polish-basis-namecert-obligations}, and \autoref{thm:polish-basis-complete-separable-handoff} seed the countable-basis certificate route supporting $\PolishSpaceUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host topologies, arbitrary open covers, selected dense points, quotient completion equality, ambient set membership, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-schedule readback, finite basis-index windowing, finite-intersection refinement, complete-separable handoff, and local naming for BEDC.Derived.PolishBasisUp.}
\end{closurestatus}
