\chapter{A Concrete Naming Certificate for $\MetricSpaceUp$}
\label{ch:concrete-instances-metric-space-namecert}
\origin{human}

Following Bishop and Bridges and Bourbaki, the $\MetricSpaceUp$ packet records the traditional metric-space interface as finite BEDC NameCert data. It sits over the generic distance-witness surface of \autoref{ch:concrete-instances-metric-namecert}, the real-valued distance route of \autoref{ch:concrete-instances-real-metric-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-name interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter gives completion, topology, total-boundedness, compactness, and Polish-space consumers a single cited carrier surface without importing quotient equality, selected limits, countable choice, or ambient completeness.

\begin{definition}[MetricSpace carrier]
\label{def:metric-space-carrier}
A $\MetricSpaceUp$ carrier is a finite $\BHist$ packet
$$
M=(X,\sigma,D,Z,S,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the point-carrier row. It names the displayed point observations and the finite windows through which downstream consumers may inspect them.
\item $\sigma$ is the point-classifier row. It records the accepted point equivalence used by $\hsame$ transport and by the zero-distance classifier handoff.
\item $D$ is the $\RealUp$-valued distance row. It is read through the $\MetricUp$ witness surface of \autoref{ch:concrete-instances-metric-namecert} and the $\RealMetricUp$ distance route of \autoref{ch:concrete-instances-real-metric-namecert}.
\item $Z$ is the zero-distance classifier row, requiring any request that turns distance zero into point equivalence to pass through $\sigma$ rather than through host equality.
\item $S$ is the symmetry row, carrying the componentwise reversal of endpoint observations and the corresponding distance readback.
\item $T$ is the triangle row, carrying the three endpoint-pair distance reads and the dyadic tolerance budget used to compose them.
\item $H$ records componentwise $\hsame$ transport for the point carrier, classifier, distance, zero-distance, symmetry, triangle, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a metric request through the finite route
$$
X,\sigma
\longmapsto
\MetricUp,\RealMetricUp
\longmapsto
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp
\longmapsto
Z,S,T,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\MetricSpaceUp$, $\MetricUp$, $\RealMetricUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,\sigma,D,Z,S,T,H,C,P,N$. It has no coordinate for host equality of points, quotient completion equality, selected representatives, countable choice, ambient $\RealUp$ completeness, or a detached topology.
\end{definition}

\begin{theorem}[MetricSpace NameCert obligations]
\label{thm:metric-space-namecert-obligations}
For every accepted $\MetricSpaceUp$ carrier
$$
M=(X,\sigma,D,Z,S,T,H,C,P,N),
$$
the local $\NameCert_{\MetricSpaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the point carrier, point classifier, real-valued distance, zero-distance classifier, symmetry, triangle, transport, replay, provenance, and local naming rows;
\item distance visibility, requiring every distance read to expose the $\MetricUp$ and $\RealMetricUp$ rows before any downstream consumer reads a real-valued metric comparison;
\item zero-distance exactness, requiring zero distance to return to the displayed classifier $\sigma$ through $Z$ and never through host point equality;
\item symmetry replay, requiring endpoint reversal to be witnessed by $S$ together with the same $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ readback route;
\item triangle-budget replay, requiring the three distance reads and their dyadic comparison budget to be displayed by $T$ before a triangle consumer may use the row;
\item structural preservation through $H,C,P,N$.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:metric-space-carrier}. An accepted packet displays the point-carrier row $X$, the classifier $\sigma$, the distance row $D$, the zero-distance row $Z$, the symmetry row $S$, the triangle row $T$, and the structural rows $H,C,P,N$.

Distance visibility is forced by the placement of $D$ in the carrier. A distance consumer first opens the generic $\MetricUp$ witness surface and the $\RealMetricUp$ readback route, and only then reads the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows needed for a finite comparison.

The zero-distance, symmetry, and triangle clauses are rowwise. The row $Z$ is the only route from distance zero back to the point classifier, $S$ is the only endpoint-reversal row, and $T$ is the only triangle-budget row.

Finally, $H,C,P,N$ transport, replay, source, and name exactly the displayed rows. Since the carrier has no other coordinate, the listed rows exhaust the local NameCert surface and cannot export host equality, quotient completion equality, selected representatives, countable choice, ambient completeness, or a detached topology.
\end{proof}

\begin{theorem}[MetricSpace distance route]
\label{thm:metric-space-distance-route}
Every completion, topology, total-boundedness, compactness, or Polish-space consumer of an accepted $\MetricSpaceUp$ carrier reads distance information through the finite route
$$
X,\sigma,D
\longmapsto
\MetricUp,\RealMetricUp
\longmapsto
\DyadicRatCoreUp,\StreamNameUp,\RegSeqRatUp,\RealUp
\longmapsto
Z,S,T,H,C,P,N .
$$
Thus the public distance surface is the displayed BEDC route from point observations and classifier data to real-valued metric reads, zero-distance classification, symmetry, and triangle replay. It exports no quotient equality, selected limit, countable-choice schedule, ambient completeness theorem, or open-set lattice.
\end{theorem}
\begin{proof}
Let a downstream consumer inspect an accepted carrier $M=(X,\sigma,D,Z,S,T,H,C,P,N)$. The point surface is opened first through $X$ and $\sigma$, so every later distance read remains attached to the displayed point classifier.

The distance row $D$ then routes the request through $\MetricUp$ and $\RealMetricUp$. The numerical readback is finite because the dyadic tolerance, stream-window, regular-rational, and real-name rows are displayed before any metric comparison is consumed.

Metric laws are read only after this route is visible. Zero distance returns through $Z$ to $\sigma$, symmetry reverses endpoints through $S$, and triangle use exposes the three pairwise reads and dyadic budget through $T$.

The structural rows $H,C,P,N$ preserve the same route under transport, replay, provenance, and local naming. Since none of the excluded objects appears in the carrier, no listed downstream consumer can read quotient equality, a selected limit, a choice schedule, ambient completeness, or an open-set lattice from the $\MetricSpaceUp$ packet.
\end{proof}

\closureat{MetricSpaceUp}{seedStr}
