\chapter{A Concrete Naming Certificate for $\HyperbolicObserverExpansionUp$}
\label{ch:concrete-instances-hyperbolic-observer-expansion-namecert}
\origin{ai}

The $\HyperbolicObserverExpansionUp$ packet realizes the observer-expansion reading of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite observer-shadow certificate data. It consumes the visual-shadow metric of \autoref{ch:concrete-instances-hyperbolic-visual-shadow-metric-namecert}, the boundary-shadow route of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, the metric surface of \autoref{ch:concrete-instances-metric-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, and the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}. The packet names an expansion-facing shadow route, not a global hyperbolic space, physical observer history, quotient boundary, or ambient field semantics.

\begin{definition}[Hyperbolic observer-expansion carrier]
\label{def:hyperbolic-observer-expansion-carrier}
A $\HyperbolicObserverExpansionUp$ carrier is a finite $\BHist$ packet
$$
E=(V,B,M,S,R,Q,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $V$ is the $\HyperbolicVisualShadowMetricUp$ source row, supplying the visual-shadow metric packet read by the observer-facing expansion route.
\item $B$ is the $\HyperbolicBoundaryShadowUp$ row that records the boundary-shadow datum inspected by the expansion packet.
\item $M$ is the $\MetricUp$ comparison row used when the shadow expansion is consumed as metric evidence.
\item $S$ is the $\StreamNameUp$ finite-window schedule for the visual-shadow, boundary-shadow, metric, and real-seal reads.
\item $R$ is the regular readback row for rational windows opened by $S$.
\item $Q$ is the terminal $\RealUp$ seal row for the displayed expansion magnitude or shadow-distance comparison.
\item $F$ is the observer-expansion row, recording the focused expansion-shadow route being inspected.
\item $H$ records componentwise $\hsame$ transport for $V,B,M,S,R,Q,F$ and the local certificate rows.
\item $C$ records displayed $\Cont$ replay from an observer-expansion request through visual-shadow metric, boundary shadow, metric comparison, stream windows, regular readback, real sealing, and focused routing.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicObserverExpansionUp$, $\HyperbolicVisualShadowMetricUp$, $\HyperbolicBoundaryShadowUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\HyperbolicObserverExpansionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $V,B,M,S,R,Q,F,H,C,P,N$. It has no coordinate for completed hyperbolic geometry, physical observers, quotient boundary equality, global field interpretation, or unlogged expansion flow.
\end{definition}

\begin{theorem}[Hyperbolic observer-expansion NameCert obligations]
\label{thm:hyperbolic-observer-expansion-namecert-obligations}
For every accepted $\HyperbolicObserverExpansionUp$ carrier
$$
E=(V,B,M,S,R,Q,F,H,C,P,N),
$$
the local $\NameCert_{\HyperbolicObserverExpansionUp}$ surface consists exactly of visual-shadow metric admission, boundary-shadow admission, metric comparison, stream-window exposure, regular readback, terminal real sealing, focused observer-expansion routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $V,B,M,S,R,Q,F,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-observer-expansion-carrier}. The rows $V,B,M,S,R,Q,F,H,C,P,N$ are the whole observer-expansion packet.

The source read begins with the visual-shadow metric row $V$ and the boundary-shadow row $B$. The metric row $M$ then gives the comparison surface on which the expansion-facing shadow is inspected.

The finite observation route is supplied by $S,R,Q$: stream windows, regular readbacks, and the terminal real seal. The focused row $F$ records which observer-expansion shadow route is being named.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no further coordinate is present, the NameCert surface exports no completed hyperbolic geometry, physical observer, quotient boundary equality, global field interpretation, or unlogged expansion flow.
\end{proof}

\begin{theorem}[Hyperbolic observer-expansion finite shadow handoff]
\label{thm:hyperbolic-observer-expansion-finite-shadow-handoff}
Every accepted $\HyperbolicObserverExpansionUp$ read factors through $\HyperbolicVisualShadowMetricUp$, $\HyperbolicBoundaryShadowUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows before the observer-expansion route can be consumed as a local $\NameCert$ datum.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $E=(V,B,M,S,R,Q,F,H,C,P,N)$. The visual-shadow metric row $V$ and boundary-shadow row $B$ present the finite shadow data.

The metric comparison $M$ is then read through finite windows $S$, regular readback $R$, and the real seal $Q$. Only after these rows are displayed does the focused route $F$ expose the observer-expansion datum.

Transport, continuation, provenance, and local naming are supplied by $H,C,P,N$. Therefore the handoff remains finite and cannot pass through completed hyperbolic geometry, physical observer history, quotient boundary equality, or ambient field semantics.
\end{proof}

\falsifiablePrediction{Every accepted hyperbolic\_observer\_expansion read factors through hyperbolic\_visual\_shadow\_metric, hyperbolic\_boundary\_shadow, metric, streamname, regular readback, real sealing, displayed replay, provenance, and local $\NameCert$ rows.}

\independenceWitness{hyperbolic\_visual\_shadow\_metric, hyperbolic\_boundary\_shadow, metric, streamname, real: no listed sibling is bijective to $\HyperbolicObserverExpansionUp$ because this packet jointly carries visual-shadow metric data, boundary-shadow data, metric comparison, finite stream windows, real sealing, focused observer-expansion routing, replay, provenance, and local naming.}

The Lean TasteGate route must provide \texttt{Nontrivial HyperbolicObserverExpansionUp} and \texttt{FieldFaithful HyperbolicObserverExpansionUp} instances in \texttt{lean4/BEDC/Derived/HyperbolicObserverExpansionUp/TasteGate.lean}. Those instances must preserve $V,B,M,S,R,Q,F,H,C,P,N$ as distinct fields before a checked carrier-alignment theorem can serve as the TasteGate witness.

\closureat{HyperbolicObserverExpansionUp}{seedStr}

\begin{closurestatus}{\HyperbolicObserverExpansionUp}
  \constructivestory{A $\HyperbolicObserverExpansionUp$ packet is generated from HyperbolicVisualShadowMetric rows, HyperbolicBoundaryShadow rows, Metric rows, StreamName windows, regular readback, Real sealing, focused observer-expansion routing, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-observer-expansion-carrier}, \autoref{thm:hyperbolic-observer-expansion-namecert-obligations}, and \autoref{thm:hyperbolic-observer-expansion-finite-shadow-handoff} seed the finite observer-shadow expansion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim completed hyperbolic geometry, physical observer histories, quotient boundary equality, global field interpretation, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, visual-shadow metric admission, boundary-shadow admission, metric comparison, stream readback, real sealing, TasteGate nontriviality, field faithfulness, and local naming for BEDC.Derived.HyperbolicObserverExpansionUp.}
\end{closurestatus}
