\chapter{A Concrete Naming Certificate for $\NestedIntervalsTheoremUp$}
\label{ch:concrete-instances-nested-intervals-theorem-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\NestedIntervalsTheoremUp$ packet records the theorem-shaped finite route by which a nested sequence of closed bounded intervals supplies a real-name witness when each displayed stage carries an explicit shrinking and containment ledger. It reads the base closed-interval source of \autoref{ch:concrete-instances-closedboundedinterval-namecert}, the nested-prefix surface of \autoref{ch:concrete-instances-nestedinterval-namecert}, the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicinterval-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the Bishop-style nested-interval theorem as a finite NameCert obligation surface; it does not assert open-cover compactness, ambient $\RealUp$ completeness, quotient equality of real names, countable choice, trichotomy, or selected host endpoints.

\begin{definition}[NestedIntervalsTheorem carrier]
\label{def:nested-intervals-theorem-carrier}
A $\NestedIntervalsTheoremUp$ carrier is a finite $\BHist$ packet
$$
T=(B,J,D,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\ClosedBoundedIntervalUp$ source row carrying lower and upper endpoint data, endpoint order, containment ledgers, finite windows, regular readback, and a real-name seal boundary.
\item $J$ is the $\NestedIntervalUp$ prefix row recording the displayed containment chain over the same interval source.
\item $D$ is the $\DyadicIntervalUp$ shrinking ledger attached to the displayed endpoints and nested-containment rows.
\item $W$ is the finite observation-window row that records which source stages and precisions are opened.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from $B,J,D,W$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the closed-bounded source, nested prefix, dyadic ledger, and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source interval, nested prefix, dyadic ledger, windows, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the theorem request through $B,J,D,W,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\NestedIntervalsTheoremUp$, $\ClosedBoundedIntervalUp$, $\NestedIntervalUp$, $\DyadicIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\NestedIntervalsTheoremUp}$ row.
\end{enumerate}
The carrier is theorem-shaped because it names the obligation route from a displayed nested closed-interval prefix to a real-name witness seal. It has no coordinate for an arbitrary open cover, selected host endpoint, quotient real equality, trichotomy decision, countable-choice selector, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge row.
\end{definition}

\begin{theorem}[NestedIntervalsTheorem NameCert obligations]
\label{thm:nested-intervals-theorem-namecert-obligations}
For every accepted $\NestedIntervalsTheoremUp$ carrier $T=(B,J,D,W,R,E,H,C,P,N)$, the local $\NameCert_{\NestedIntervalsTheoremUp}$ surface consists exactly of carrier admission for the closed-bounded interval source $B$, the nested-prefix row $J$, the dyadic shrinking ledger $D$, the finite observation windows $W$, regular rational readback $R$, terminal $\RealUp$ seal $E$, componentwise transport $H$, displayed replay $C$, provenance $P$, and local naming $N$. Every Real-facing witness read must pass through $B,J,D,W,R$ before $E$ is visible, and no obligation may be discharged by open-cover compactness, ambient real completeness, quotient equality, countable choice, trichotomy, or selected host endpoints.
\end{theorem}
\leanchecked{BEDC.Derived.NestedIntervalsTheoremUp.NestedIntervalsTheoremTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier of \autoref{def:nested-intervals-theorem-carrier}. The displayed analytic rows are the closed-bounded source $B$, nested-prefix row $J$, dyadic shrinking ledger $D$, finite window row $W$, regular readback $R$, and terminal seal $E$.

The witness route is ordered by those rows. The closed-bounded source supplies endpoint order and containment, the nested-prefix row supplies inclusion, the dyadic ledger supplies shrinking data, and the finite observation windows determine the regular rational readback before the Real seal can be consumed.

The structural rows add no hidden theorem. Transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ preserve the same finite route. Since the carrier has no coordinate for open-cover compactness, ambient completeness, quotient equality, countable choice, trichotomy, or selected endpoints, the listed rows exhaust the NameCert obligations.
\end{proof}

\closureat{NestedIntervalsTheoremUp}{seedStr}

\begin{closurestatus}{\NestedIntervalsTheoremUp}
  \constructivestory{A $\NestedIntervalsTheoremUp$ packet is generated from a ClosedBoundedIntervalUp source row, a NestedIntervalUp prefix, a DyadicIntervalUp shrinking ledger, finite observation windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nested-intervals-theorem-carrier} and \autoref{thm:nested-intervals-theorem-namecert-obligations} seed the Bishop-style nested-interval theorem route as finite NameCert data over closed bounded intervals, nested prefixes, dyadic ledgers, regular rational readback, and real-name seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, ambient $\RealUp$ completeness, quotient real equality, trichotomy, countable choice, selected host endpoints, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, nested-prefix containment, dyadic shrinking, finite-window readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.NestedIntervalsTheoremUp.}
\end{closurestatus}
