\chapter{A Concrete Naming Certificate for $\SeparableRealUp$}
\label{ch:concrete-instances-separable-real-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\SeparableRealUp$ packet records separability as a finite NameCert surface over dyadic schedules rather than as host enumeration or countable choice. It sits over the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the rational carrier of \autoref{ch:concrete-instances-rat-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the existing real separability route of \autoref{ch:concrete-instances-real-separability-namecert}. The packet names the constructive dense schedule visible to Real and Completion consumers; it is not a quotient-real equality principle, a selected host list of all reals, a trichotomy oracle, or an assertion of ambient $\RealUp$ completeness.

\begin{definition}[SeparableReal carrier]
\label{def:separable-real-carrier}
A $\SeparableRealUp$ carrier is a finite $\BHist$ packet
$$
S=(D,S_0,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ dense-schedule row, recording the finite dyadic centers and tolerance budgets inspected by a separability request.
\item $S_0$ is the $\StreamNameUp$ finite-window row, naming the observation windows through which the dense schedule is read.
\item $R$ is the $\RegSeqRatUp$ readback row, exposing regular rational approximants attached to the same windows and dyadic budgets.
\item $Q$ is the $\RatUp$ and $\DyadicRatCoreUp$ tolerance row, recording rational comparison data only at the displayed dyadic precision.
\item $E$ is the terminal $\RealUp$ seal row, reached only after the schedule, window, readback, and tolerance rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the dense schedule, finite windows, readback, tolerance, seal, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from a separability query through $D,S_0,R,Q,E$.
\item $P$ is the $\Pkg$ provenance over $\SeparableRealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SeparableRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S_0,R,Q,E,H,C,P,N$. It has no coordinate for host enumeration of $\RealUp$, countable choice, quotient real equality, trichotomy of real order, hidden completion data, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[SeparableReal dyadic density NameCert]
\label{thm:separable-real-dyadic-density-namecert}
For every accepted $\SeparableRealUp$ carrier
$$
S=(D,S_0,R,Q,E,H,C,P,N),
$$
the local $\NameCert_{\SeparableRealUp}$ surface exposes density only by the finite dyadic schedule $D$, the finite $\StreamNameUp$ windows $S_0$, the $\RegSeqRatUp$ readback row $R$, the rational and dyadic tolerance row $Q$, and the terminal $\RealUp$ seal $E$. The remaining rows $H,C,P,N$ provide componentwise transport, displayed replay, package provenance, and local naming for that same route.

Consequently an accepted packet supplies a separability witness for Real and Completion consumers without host enumeration, countable choice, quotient real equality, real-order trichotomy, hidden completion data, or a completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separable-real-carrier}. The tuple lists exactly the dense dyadic schedule, finite observation windows, regular rational readback, rational tolerance data, terminal Real seal, transport, replay, provenance, and local naming rows.

The density route is fixed before any real-name consumer reads it. A separability query first opens the dyadic schedule row $D$ and the finite window row $S_0$, then reads the regular rational approximants in $R$ against the tolerance row $Q$.

The terminal Real seal $E$ is downstream of those displayed rows, so a consumer never receives an unsealed host real or a selected quotient representative. The structural rows $H,C,P,N$ transport, replay, source, and name only the same displayed data.

Since the carrier contains no coordinate for host enumeration, countable choice, quotient equality, trichotomy, hidden completion data, or ambient completeness, the listed rows exhaust the local NameCert surface. The accepted packet therefore exposes density only through the finite dyadic schedule and the $\RealUp$ seal.
\end{proof}

\closureat{SeparableRealUp}{seedStr}

\begin{closurestatus}{\SeparableRealUp}
  \constructivestory{A $\SeparableRealUp$ packet is generated from a dyadic dense schedule, finite StreamName windows, RegSeqRat readback, Rat and DyadicRatCore tolerance rows, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:separable-real-carrier} and \autoref{thm:separable-real-dyadic-density-namecert} seed the finite dyadic density surface for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host enumeration, countable choice, quotient real equality, real-order trichotomy, hidden completion data, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic density schedule exposure, StreamName window replay, RegSeqRat readback, Rat and DyadicRatCore tolerance exactness, Real seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.SeparableRealUp.}
\end{closurestatus}
