\chapter{A Concrete Naming Certificate for $\HyperbolicVisualBoundaryUp$}
\label{ch:concrete-instances-hyperbolic-visual-boundary-namecert}
\origin{ai}

The $\HyperbolicVisualBoundaryUp$ packet realizes the finite boundary-readback surface of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion}. It sits after the metric-read surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the Busemann-boundary row of \autoref{ch:concrete-instances-hyperbolic-busemann-boundary-namecert}, the visual-metric packet of \autoref{ch:concrete-instances-hyperbolic-visual-metric-namecert}, the boundary-shadow packet of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, and the boundary-fixed transport route of \autoref{ch:concrete-instances-poincare-boundary-fixed-transport-namecert}. The packet names only a finite visual boundary read over displayed disk, shadow, Busemann, visual-metric, transport, provenance, and local naming rows; it does not assert physical cosmology, a completed ideal-boundary quotient, global geometry, or a host compactification theorem.

\begin{definition}[Hyperbolic visual boundary carrier]
\label{def:hyperbolic-visual-boundary-carrier}
A $\HyperbolicVisualBoundaryUp$ carrier is a finite $\BHist$ packet
$$
V=(D,S,B,M,T,P,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the disk-readout row, exposing the finite $\UnitDiskUp$ or Poincare-disk observation window from which the boundary read begins.
\item $S$ is the boundary-shadow row, recording the $\HyperbolicBoundaryShadowUp$ face visible from the disk readout.
\item $B$ is the Busemann row, attaching the boundary read to $\HyperbolicBusemannBoundaryUp$ distance-difference data.
\item $M$ is the visual-metric row, recording the $\HyperbolicVisualMetricUp$ comparison used to distinguish visible boundary reads.
\item $T$ is the transport row, recording the $\PoincareBoundaryFixedTransportUp$ route that preserves the boundary read while disk data move.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicVisualBoundaryUp$, $\HyperbolicMetricUp$, $\HyperbolicBusemannBoundaryUp$, $\HyperbolicVisualMetricUp$, $\HyperbolicBoundaryShadowUp$, $\PoincareBoundaryFixedTransportUp$, $\UnitDiskUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $H$ records componentwise $\hsame$ transport for disk-readout, boundary-shadow, Busemann, visual-metric, transport, provenance, replay, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a boundary-read request through $D,S,B,M,T,P,H$.
\item $N$ is the local $\NameCert_{\HyperbolicVisualBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S,B,M,T,P,H,C,N$. It has no coordinate for a completed boundary space, quotient ideal-end equality, physical observer trajectory, global hyperbolic geometry, or an unlogged cosmological claim.
\end{definition}

\begin{theorem}[Hyperbolic visual boundary NameCert obligations]
\label{thm:hyperbolic-visual-boundary-namecert-obligations}
For every accepted $\HyperbolicVisualBoundaryUp$ carrier
$$
V=(D,S,B,M,T,P,H,C,N),
$$
the local $\NameCert_{\HyperbolicVisualBoundaryUp}$ surface consists exactly of disk-readout admission, boundary-shadow exposure, Busemann attachment, visual-metric comparison, boundary-fixed transport, provenance, componentwise transport, displayed continuation replay, and local naming through $D,S,B,M,T,P,H,C,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-visual-boundary-carrier}. The rows $D,S,B,M,T,P,H,C,N$ are the whole public packet.

The read starts at $D$ and $S$. These rows expose only a finite disk window and a displayed boundary-shadow face.

The Busemann and visual-metric rows $B,M$ attach that face to finite boundary comparison data. The transport row $T$ records boundary-fixed movement without adding a completed boundary object.

Finally $P,H,C,N$ source, transport, replay, and name the same route. Since no other coordinate is present, completed boundary spaces, quotient ideal-end equality, physical observer trajectories, global hyperbolic geometry, and unlogged cosmological claims remain outside the certificate.
\end{proof}

\begin{theorem}[Hyperbolic visual boundary readback non-escape]
\label{thm:hyperbolic-visual-boundary-readback-nonescape}
Every accepted $\HyperbolicVisualBoundaryUp$ read factors through
$$
\HyperbolicMetricUp,\ \HyperbolicBusemannBoundaryUp,\ \HyperbolicVisualMetricUp,\ \HyperbolicBoundaryShadowUp,\ \PoincareBoundaryFixedTransportUp
$$
together with disk-readout, provenance, transport, replay, and local $\NameCert$ rows before it exports a visual boundary token.
\end{theorem}
\begin{proof}
Apply \autoref{thm:hyperbolic-visual-boundary-namecert-obligations}. The accepted packet stores boundary readback only in the displayed rows $D,S,B,M,T,P,H,C,N$.

The metric, Busemann, visual-metric, shadow, and fixed-transport siblings are named by those rows and by provenance. A consumer therefore receives a boundary token only after the finite route has exposed those dependencies.

No row in the carrier stores physical cosmology, completed ideal-boundary equality, global geometry, or a host compactification theorem. Hence an accepted read cannot bypass the displayed packet through any of those exits.
\end{proof}

\falsifiablePrediction{Every accepted $\HyperbolicVisualBoundaryUp$ read is refuted if a consumer obtains a visual boundary token without displaying hyperbolicmetric, hyperbolic-busemann-boundary, hyperbolic-visual-metric, hyperbolic-boundary-shadow, poincare-boundary-fixed-transport, disk-readout, provenance, transport, replay, and local $\NameCert$ rows.}

\independenceWitness{hyperbolicmetric, hyperbolic-busemann-boundary, hyperbolic-visual-metric, hyperbolic-boundary-shadow, poincare-boundary-fixed-transport: the HyperbolicMetric packet records metric reads without boundary readback, the Busemann packet records distance-difference boundary data without a visual-boundary token, the visual-metric packet records comparison without owning the boundary row, the boundary-shadow packet records a shadow face without the Busemann visual comparison, and the boundary-fixed transport packet preserves a boundary route without naming the visual boundary carrier. None is bijective to $\HyperbolicVisualBoundaryUp$.}

\closureat{HyperbolicVisualBoundaryUp}{seedStr}

\begin{closurestatus}{\HyperbolicVisualBoundaryUp}
  \constructivestory{A $\HyperbolicVisualBoundaryUp$ packet is generated from disk-readout rows, HyperbolicBoundaryShadow rows, HyperbolicBusemannBoundary rows, HyperbolicVisualMetric rows, PoincareBoundaryFixedTransport rows, provenance, componentwise hsame transport, displayed Cont replay, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-visual-boundary-carrier}, \autoref{thm:hyperbolic-visual-boundary-namecert-obligations}, and \autoref{thm:hyperbolic-visual-boundary-readback-nonescape} seed the finite visual boundary readback route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close physical cosmology, completed ideal-boundary quotients, global hyperbolic geometry, host compactification, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked disk readback, shadow exposure, Busemann attachment, visual-metric comparison, boundary-fixed transport, provenance, replay, transport, and local naming for BEDC.Derived.HyperbolicVisualBoundaryUp.}
\end{closurestatus}
