\chapter{A Concrete Naming Certificate for $\DefectFlowPartitionSkeletonUp$}
\label{ch:concrete-instances-defect-flow-partition-skeleton-namecert}
\origin{ai}

The $\DefectFlowPartitionSkeletonUp$ packet realizes the defect-flow partition skeleton of \autoref{thm:philosophy-defect-flow-partition-skeleton} as finite cubical-incidence and boundary-flow NameCert data. It sits over the partition carrier of \autoref{ch:concrete-instances-partition-namecert}, the cellular-update surface of \autoref{ch:concrete-instances-cellularautomaton-namecert}, the Boolean row discipline of \autoref{ch:concrete-instances-booleanalgebra-namecert}, the rank-dependence boundary of \autoref{ch:concrete-instances-matroid-namecert}, and the support-nerve surface of \autoref{ch:concrete-instances-simplicialcomplex-namecert}. The packet names the finite route from partition blocks and boundary incidences to defect-lowering transitions; it is not a host graph-flow oracle, stochastic biological model, quotient codon semantics, unrestricted homology computation, or hidden global scheduler.

\begin{definition}[Defect-flow partition skeleton carrier]
\label{def:defect-flow-partition-skeleton-carrier}
A $\DefectFlowPartitionSkeletonUp$ carrier is a finite $\BHist$ packet
$$
S=(B,I,L,T,A,M,X,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the finite partition-block row, listing the displayed sink blocks and their support names.
\item $I$ is the cubical boundary-incidence row, recording which displayed boundary faces meet each block.
\item $L$ is the defect-level ledger, recording the finite defect value attached to each non-sink incidence state.
\item $T$ is the defect-flow transition row, listing the allowed defect-lowering moves between displayed states.
\item $A$ is the $\CellularAutomatonUp$ local update row used to replay $T$ as a finite boundary-flow step.
\item $M$ is the $\MatroidUp$ rank-dependence row separating removable shared incidences from protected private coordinates.
\item $X$ is the $\SimplicialComplexUp$ and $\BooleanAlgebraUp$ support-nerve row, exposing faces, complements, and Boolean incidence tests.
\item $H$ stores componentwise $\hsame$ transport for $B,I,L,T,A,M,X,C,P,N$.
\item $C$ stores displayed $\Cont$ replay from a boundary-flow request through the same finite rows.
\item $P$ is the $\Pkg$ provenance over $\DefectFlowPartitionSkeletonUp$, $\PartitionUp$, $\CellularAutomatonUp$, $\BooleanAlgebraUp$, $\MatroidUp$, $\SimplicialComplexUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DefectFlowPartitionSkeletonUp}$ row.
\end{enumerate}
The carrier has no coordinate for unrestricted flow search, host graph reachability, quotient codon semantics, biological stochastic semantics, hidden scheduler state, or unrestricted homology.
\end{definition}

\begin{theorem}[Defect-flow partition skeleton NameCert obligations]
\label{thm:defect-flow-partition-skeleton-namecert-obligations}
For every accepted $\DefectFlowPartitionSkeletonUp$ carrier
$$
S=(B,I,L,T,A,M,X,H,C,P,N),
$$
the local $\NameCert_{\DefectFlowPartitionSkeletonUp}$ surface consists exactly of carrier admission for partition blocks, cubical boundary-incidence rows, defect-level ledgers, defect-flow transitions, cellular replay, matroid rank-dependence separation, Boolean and simplicial support-nerve tests, componentwise transport, displayed continuation replay, provenance, and local naming.

A boundary-flow consumer may read a transition in $T$ only after the source block row $B$, incidence row $I$, and defect ledger $L$ have been displayed, and it may classify a sink only through the partition row and the support-nerve row. No obligation in the packet is discharged by host reachability, unrestricted flow search, biological stochastic semantics, quotient codon semantics, or hidden global scheduling.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:defect-flow-partition-skeleton-carrier}. The displayed tuple lists the partition, incidence, defect, transition, cellular replay, rank-dependence, support-nerve, transport, continuation, provenance, and naming rows.

The transition order is fixed by the finite route. A consumer first reads the partition blocks $B$ and cubical incidences $I$, then reads the defect ledger $L$, and only then may inspect the defect-lowering transition row $T$.

The cellular, matroid, Boolean, and simplicial rows explain how the same finite transition is replayed and classified. They provide local update, protected-coordinate separation, complement tests, and support-nerve exposure without importing a host flow oracle.

Finally $H,C,P,N$ keep all reads inside the displayed packet. Since no excluded reachability, stochastic, quotient, scheduler, or unrestricted homology coordinate is present, the stated obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Defect-flow partition skeleton TasteGate boundary]
\label{thm:defect-flow-partition-skeleton-tastegate-boundary}
Any future TasteGate surface for $\DefectFlowPartitionSkeletonUp$ must provide $\mathsf{Nontrivial}\ \DefectFlowPartitionSkeletonUp$ and $\mathsf{FieldFaithful}\ \DefectFlowPartitionSkeletonUp$ instances preserving $B,I,L,T,A,M,X,H,C,P,N$ as separate displayed fields. In particular, the gate must distinguish a changed partition block, a changed boundary-incidence row, a changed defect-flow transition, and a changed support-nerve row before it admits the packet as the same skeleton.
\end{theorem}
\begin{proof}
Use the carrier of \autoref{def:defect-flow-partition-skeleton-carrier}. The rows $B,I,L,T,A,M,X$ play different roles in the finite boundary-flow route: source blocks, boundary incidences, defect values, transitions, cellular replay, rank separation, and support-nerve classification.

The NameCert obligations of \autoref{thm:defect-flow-partition-skeleton-namecert-obligations} consume those rows in order. Identifying two of them would erase either the source, the flow step, or the classification boundary, so a field-faithful gate must preserve the displayed coordinates separately.

Nontriviality is witnessed by packets that vary one of the displayed rows while keeping the structural rows fixed. Such packets are observable at the carrier boundary and therefore cannot be collapsed by an admissible TasteGate read.
\end{proof}

\falsifiablePrediction{Every accepted $\DefectFlowPartitionSkeletonUp$ read must expose partition blocks, cubical boundary-incidence rows, defect-level ledgers, defect-flow transitions, a cellular replay row, matroid rank-dependence separation, Boolean and simplicial support-nerve tests, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before a boundary-flow consumer reads a partition sink.}

\independenceWitness{partition, cellularautomaton, booleanalgebra, matroid, simplicialcomplex: none alone is bijective with $\DefectFlowPartitionSkeletonUp$ because the packet jointly carries partition blocks, boundary incidences, defect transitions, update replay, rank separation, support-nerve tests, transport, replay, provenance, and local NameCert rows.}

\closureat{DefectFlowPartitionSkeletonUp}{seedStr}

\begin{closurestatus}{\DefectFlowPartitionSkeletonUp}
  \constructivestory{A $\DefectFlowPartitionSkeletonUp$ packet is generated from partition-block rows, cubical boundary-incidence rows, defect-level ledgers, defect-flow transition rows, cellular replay, matroid rank-dependence separation, Boolean and simplicial support-nerve tests, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:defect-flow-partition-skeleton-carrier}, \autoref{thm:defect-flow-partition-skeleton-namecert-obligations}, and \autoref{thm:defect-flow-partition-skeleton-tastegate-boundary} seed the finite defect-flow partition skeleton packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim unrestricted flow search, biological stochastic semantics, quotient codon semantics, unrestricted homology, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, transition exactness, sink classification, Nontrivial DefectFlowPartitionSkeletonUp, and FieldFaithful DefectFlowPartitionSkeletonUp for BEDC.Derived.DefectFlowPartitionSkeletonUp.}
\end{closurestatus}
