\chapter{A Concrete Naming Certificate for $\NowhereDenseUp$}
\label{ch:concrete-instances-nowhere-dense-namecert}
\origin{human}

Following Baire and Oxtoby, a nowhere-dense component is treated here as the finite certificate surface that lets Baire-category arguments read a closed-frontier refusal without importing arbitrary subset quantification. The $\NowhereDenseUp$ packet sits between the topology carrier of \autoref{ch:concrete-instances-topology-namecert}, the dense-open route of \autoref{ch:concrete-instances-bairecategory-namecert}, and the finite cover ledger consumed by \autoref{ch:concrete-instances-meagre-set-namecert}.

\begin{definition}[Nowhere-dense carrier]
\label{def:nowhere-dense-carrier}
A $\NowhereDenseUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,B,F,E,D,M,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\TopologyUp$ source row, including the basic-neighbourhood names inspected by the packet.
\item $B$ is the finite basic-neighbourhood request ledger over $T$.
\item $F$ is the closure-frontier row naming how inspected neighbourhoods meet the displayed closure boundary.
\item $E$ is the empty-interior refusal row; for every requested basic neighbourhood it displays a sub-neighbourhood escaping the named closed fragment.
\item $D$ is the dense-open complement handoff read by $\BaireCategoryUp$ consumers.
\item $M$ is the finite cover-row interface consumed by $\MeagreSetUp$.
\item $H$ stores the componentwise $\hsame$ transports for $T,B,F,E,D,M$.
\item $C$ stores displayed $\Cont$ replay of the neighbourhood requests, closure-frontier inspections, empty-interior refusals, and dense-open handoff.
\item $P$ is the local $\Pkg$ provenance row tying the packet to the named topology source.
\item $N$ is the local $\NameCert$ row for the displayed nowhere-dense component.
\end{enumerate}
The carrier exports no arbitrary subset classifier, host closure operator, selected generic point, countable-choice selector, or ambient Baire theorem.
\end{definition}

\begin{theorem}[NowhereDense NameCert obligations]
\label{thm:nowhere-dense-namecert-obligations}
Every accepted $\NowhereDenseUp$ carrier $Q=(T,B,F,E,D,M,H,C,P,N)$ supplies exactly the topology source, basic-neighbourhood ledger, closure-frontier row, empty-interior refusal row, dense-open complement handoff, meagre-set cover interface, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row listed in \autoref{def:nowhere-dense-carrier}. A $\BaireCategoryUp$ or $\MeagreSetUp$ consumer can read the component only through those rows.
\end{theorem}
\begin{proof}
Open the carrier definition. Each coordinate of $Q$ is a finite row, and the topology source $T$ is the only source from which basic neighbourhoods may be requested.

The closure-frontier and empty-interior rows are then read as paired inspections: $F$ names the frontier contact and $E$ supplies the escaping sub-neighbourhood. The dense-open complement row $D$ and meagre cover row $M$ are downstream of those inspections.

Finally $H,C,P,N$ preserve, replay, source, and name the same route. Since no arbitrary subset classifier, host closure operator, generic point selector, or countable-choice coordinate occurs in $Q$, downstream Baire-category and meagre-set consumers receive exactly the displayed finite packet.
\end{proof}

\begin{theorem}[NowhereDense closure-interior refusal]
\label{thm:nowhere-dense-closure-interior-refusal}
Let $Q=(T,B,F,E,D,M,H,C,P,N)$ be an accepted $\NowhereDenseUp$ carrier. For every basic-neighbourhood request recorded by $B$, the packet routes the request through the closure-frontier row $F$ and then through the empty-interior refusal row $E$, producing the dense-open complement handoff $D$ used by $\BaireCategoryUp$ and the cover-row interface $M$ used by $\MeagreSetUp$.
\end{theorem}
\begin{proof}
Begin with a displayed request in $B$. The row is indexed over the same topology source $T$, so it has access only to the named basic-neighbourhood surface.

Read $F$ next. It identifies the closure-frontier inspection attached to the request. Then read $E$, which displays a sub-neighbourhood escaping the named closed fragment and therefore records empty interior on the inspected finite surface.

The complement handoff $D$ and cover interface $M$ are built from that same refusal. Transport, replay, provenance, and local naming do not alter the request; they keep the Baire-category and meagre-set consumers on the displayed route.
\end{proof}

\begin{closurestatus}{\NowhereDenseUp}
  \constructivestory{A $\NowhereDenseUp$ packet is generated from a $\TopologyUp$ source, finite basic-neighbourhood requests, a closure-frontier row, an empty-interior refusal row, a dense-open complement handoff, a $\MeagreSetUp$ cover interface, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nowhere-dense-carrier}, \autoref{thm:nowhere-dense-namecert-obligations}, and \autoref{thm:nowhere-dense-closure-interior-refusal} seed the finite closure-frontier and empty-interior refusal route consumed by Baire-category and meagre-set packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary subset closure, host interior operators, selected generic points, countable choice, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove the finite closure-frontier, empty-interior refusal, dense-open complement, and cover-interface obligations.}
\end{closurestatus}
