\chapter{A Concrete Naming Certificate for $\HyperbolicPhaseObserverExpansionUp$}
\label{ch:concrete-instances-hyperbolic-phase-observer-expansion-namecert}
\origin{ai}

The $\HyperbolicPhaseObserverExpansionUp$ packet realizes the focused-ledger, shadow-metric, boundary-shadow, and Cont-growth route of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits after the metric-read surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the observer-shadow metric row of \autoref{ch:concrete-instances-hyperbolic-observer-shadow-metric-namecert}, the boundary-shadow packet of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, the Poincare-disk dynamics route of \autoref{ch:concrete-instances-poincare-disk-dynamics-namecert}, and the finite dynamics rows of \autoref{ch:concrete-instances-dynsystem-namecert}. The packet names only an observer-expansion read over displayed disk, shadow, boundary, growth, provenance, and local naming rows; it does not assert physical cosmology, global expansion, completed boundary geometry, or an unlogged observer.

\begin{definition}[Hyperbolic phase observer-expansion carrier]
\label{def:hyperbolic-phase-observer-expansion-carrier}
A $\HyperbolicPhaseObserverExpansionUp$ carrier is a finite $\BHist$ packet
$$
E=(F,D,S,B,G,P,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the focused-ledger row, recording the finite observer-facing history slice to be read.
\item $D$ is the disk-readout row, exposing the Poincare disk window and its displayed phase coordinates.
\item $S$ is the shadow-metric row supplied by $\HyperbolicObserverShadowMetricUp$ over the same observer slice.
\item $B$ is the boundary-shadow row supplied by $\HyperbolicBoundaryShadowUp$ for the visible boundary face.
\item $G$ is the Cont-growth row, recording the finite $\DynSystemUp$ and $\PoincareDiskDynamicsUp$ replay by which the observer read expands through displayed disk stages.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicPhaseObserverExpansionUp$, $\HyperbolicMetricUp$, $\HyperbolicObserverShadowMetricUp$, $\HyperbolicBoundaryShadowUp$, $\PoincareDiskDynamicsUp$, $\DynSystemUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $H$ records componentwise $\hsame$ transport for focused-ledger, disk-readout, shadow-metric, boundary-shadow, growth, provenance, replay, and naming rows.
\item $C$ records displayed $\Cont$ replay from an observer-expansion request through $F,D,S,B,G,P,H$.
\item $N$ is the local $\NameCert_{\HyperbolicPhaseObserverExpansionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,D,S,B,G,P,H,C,N$. It has no coordinate for physical expansion, completed boundary quotient, global hyperbolic geometry, host observer identity, or unlogged cosmological data.
\end{definition}

\begin{theorem}[Hyperbolic phase observer-expansion NameCert obligations]
\label{thm:hyperbolic-phase-observer-expansion-namecert-obligations}
For every accepted $\HyperbolicPhaseObserverExpansionUp$ carrier
$$
E=(F,D,S,B,G,P,H,C,N),
$$
the local $\NameCert_{\HyperbolicPhaseObserverExpansionUp}$ surface consists exactly of focused-ledger admission, disk-readout exposure, shadow-metric comparison, boundary-shadow display, Cont-growth replay, provenance, componentwise transport, displayed continuation replay, and local naming through $F,D,S,B,G,P,H,C,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-phase-observer-expansion-carrier}. The rows $F,D,S,B,G,P,H,C,N$ are the complete public packet.

The observer-facing read begins with $F$ and $D$. These rows expose a finite ledger slice and a displayed disk window before any expansion token is available.

The shadow rows $S$ and $B$ then attach the observer slice to finite metric and boundary-shadow data. The growth row $G$ records the Poincare-disk and dynamics replay that the consumer may inspect.

Finally $P,H,C,N$ source, transport, replay, and name the same route. Since no other coordinate is present, physical expansion, completed boundary geometry, global hyperbolic structure, host observer identity, and unlogged cosmological claims remain outside the certificate.
\end{proof}

\begin{theorem}[Hyperbolic phase observer-expansion nonescape]
\label{thm:hyperbolic-phase-observer-expansion-nonescape}
Every accepted $\HyperbolicPhaseObserverExpansionUp$ read factors through hyperbolic-metric, hyperbolic-observer-shadow-metric, hyperbolic-boundary-shadow, poincare-disk-dynamics, and dynsystem rows together with focused-ledger, disk-readout, Cont-growth, provenance, transport, replay, and local $\NameCert$ data before it exports an observer-expansion token.
\end{theorem}
\begin{proof}
Apply \autoref{thm:hyperbolic-phase-observer-expansion-namecert-obligations}. The accepted packet stores observer expansion only in the displayed rows $F,D,S,B,G,P,H,C,N$.

The sibling metric, shadow, boundary, disk-dynamics, and dynamics surfaces are named by $S,B,G$ and by provenance. A consumer therefore receives an observer-expansion token only after the finite route has displayed those dependencies.

No row in the carrier stores physical cosmology, completed boundary equality, global geometry, host observer identity, or an unlogged expansion source. Hence an accepted read cannot bypass the displayed packet through any of those exits.
\end{proof}

\falsifiablePrediction{Every accepted $\HyperbolicPhaseObserverExpansionUp$ read is refuted if a consumer obtains an observer-expansion token without displaying focused-ledger, disk-readout, shadow-metric, boundary-shadow, Cont-growth, provenance, and local $\NameCert$ rows.}

\independenceWitness{hyperbolic-metric, hyperbolic-observer-shadow-metric, hyperbolic-boundary-shadow, poincare-disk-dynamics, dynsystem: the HyperbolicMetric packet records metric reads without observer expansion, the observer-shadow metric packet records shadow comparison without boundary growth, the boundary-shadow packet records a visible boundary face without disk dynamics, the Poincare-disk dynamics packet records disk replay without owning the observer ledger, and the DynSystem packet records finite dynamics without naming the hyperbolic phase observer-expansion carrier. None is bijective to $\HyperbolicPhaseObserverExpansionUp$.}

\closureat{HyperbolicPhaseObserverExpansionUp}{seedStr}

\begin{closurestatus}{\HyperbolicPhaseObserverExpansionUp}
  \constructivestory{A $\HyperbolicPhaseObserverExpansionUp$ packet is generated from focused-ledger rows, disk-readout rows, hyperbolic observer-shadow metric rows, boundary-shadow rows, Poincare-disk dynamics rows, DynSystem growth replay, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-phase-observer-expansion-carrier}, \autoref{thm:hyperbolic-phase-observer-expansion-namecert-obligations}, and \autoref{thm:hyperbolic-phase-observer-expansion-nonescape} seed the finite observer-expansion readback route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close physical cosmology, completed boundary quotients, global hyperbolic geometry, host observer identity, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked focused-ledger admission, disk-readout exposure, shadow-metric and boundary-shadow exactness, Cont-growth replay, provenance, transport, and local naming for BEDC.Derived.HyperbolicPhaseObserverExpansionUp.}
\end{closurestatus}
