\chapter{A Concrete Naming Certificate for $\MinimalTriggerOrbitClassificationUp$}
\label{ch:concrete-instances-minimal-trigger-orbit-classification-namecert}
\origin{ai}

The $\MinimalTriggerOrbitClassificationUp$ packet realizes \autoref{thm:philosophy-nine-orbit-minimal-trigger-classification} as finite BEDC NameCert data. It sits after the DNA boundary-tile source of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the lift-fiber packet of \autoref{ch:concrete-instances-minimal-trigger-lift-bundle-namecert}, the homology-core packet of \autoref{ch:concrete-instances-minimal-trigger-homology-core-namecert}, and the window coverage algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}. The packet records nine normal forms, defect rows, quotient and codon counts, transport, replay, provenance, and local naming as displayed finite rows; it is not a biological stochastic model, hidden codon semantics, unrestricted orbit enumeration, or an unrecorded homology computation.

\begin{definition}[MinimalTriggerOrbitClassification carrier]
\label{def:minimal-trigger-orbit-classification-carrier}
A $\MinimalTriggerOrbitClassificationUp$ carrier is a finite $\BHist$ packet
$$
O=(B,N,D,Q,K,L,M,H,C,P,R)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\DnaWindowSixBoundaryTileUp$ source row for the six-coordinate boundary-tile window.
\item $N$ is the nine-normal-form ledger, displaying the orbit representatives of the minimal-trigger classification.
\item $D$ is the defect ledger for the partition, single-overlap, double-overlap, and triple-overlap rows.
\item $Q$ is the quotient-count row, preserving the $49$ quotient-level minimal full triggers.
\item $K$ is the codon-count row, preserving the two-lift total $294$.
\item $L$ is the $\MinimalTriggerLiftBundleUp$ handoff row for lift-fiber decomposition.
\item $M$ is the $\MinimalTriggerHomologyCoreUp$ handoff row for support-nerve core reads.
\item $H$ records componentwise $\hsame$ transport for the source, normal-form, defect, count, handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from boundary-tile windows through normal forms, defect rows, quotient counts, codon counts, lift fibers, and homology-core handoffs.
\item $P$ is the $\Pkg$ provenance over $\MinimalTriggerOrbitClassificationUp$, $\DnaWindowSixBoundaryTileUp$, $\MinimalTriggerLiftBundleUp$, $\MinimalTriggerHomologyCoreUp$, $\WindowCoverageTriggerAlgebraUp$, the source classification theorem, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $R$ is the local $\NameCert_{\MinimalTriggerOrbitClassificationUp}$ row.
\end{enumerate}
The carrier has no coordinate for an empirical genetic-code law, a stochastic fitness model, quotient codon semantics outside the displayed rows, an unrestricted orbit search, or an external homology oracle.
\end{definition}

\begin{theorem}[MinimalTriggerOrbitClassification NameCert obligations]
\label{thm:minimal-trigger-orbit-classification-namecert-obligations}
For every accepted $\MinimalTriggerOrbitClassificationUp$ carrier $O=(B,N,D,Q,K,L,M,H,C,P,R)$, the local $\NameCert_{\MinimalTriggerOrbitClassificationUp}$ surface consists exactly of boundary-tile source admission, nine-normal-form exposure, defect-ledger exposure, quotient-count preservation, codon-count preservation, lift-bundle handoff, homology-core handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Any consumer preserving the packet must preserve the nine normal forms, the quotient count $49$, and the codon count $294$ through those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:minimal-trigger-orbit-classification-carrier}. The row $B$ supplies the boundary-tile source, while $N,D,Q,K$ display the normal forms, defects, quotient count, and codon count.

The lift and homology consumers are the rows $L$ and $M$. They can read the classification only after the finite normal-form and count rows have been displayed, so neither handoff becomes an independent orbit enumeration.

Transport and replay are carried by $H$ and $C$. These rows preserve the same displayed source, normal-form, defect, count, lift, and homology data componentwise under $\hsame$ and $\Cont$.

Finally, $P$ and $R$ source and name exactly this finite packet. Since no excluded empirical, stochastic, quotient-semantics, unrestricted-search, or external-homology coordinate is present, the listed rows exhaust the NameCert obligations and force preservation of the nine forms and the counts $49$ and $294$.
\end{proof}

\begin{theorem}[MinimalTriggerOrbitClassification vision handoff]
\label{thm:minimal-trigger-orbit-classification-vision-handoff}
The finite classification of \autoref{thm:philosophy-nine-orbit-minimal-trigger-classification} is consumed by $\MinimalTriggerOrbitClassificationUp$ only through the route
$$
\DnaWindowSixBoundaryTileUp,\ \WindowCoverageTriggerAlgebraUp
\longmapsto
N,D,Q,K
\longmapsto
\MinimalTriggerLiftBundleUp,\ \MinimalTriggerHomologyCoreUp
\longmapsto
H,C,P,R .
$$
Future Lean TasteGate files for this packet must provide explicit $\Nontrivial\ \MinimalTriggerOrbitClassificationUp$ and $\FieldFaithful\ \MinimalTriggerOrbitClassificationUp$ obligations before the packet can serve as a verified trigger-classification consumer.
\end{theorem}
\begin{proof}
Start from \autoref{thm:minimal-trigger-orbit-classification-namecert-obligations}. It places the boundary-tile and coverage-algebra source rows before any normal-form or count row can be consumed.

The middle block $N,D,Q,K$ is the finite classification ledger. It records the nine normal forms, their defect classes, the quotient count, and the codon count without opening an unrestricted orbit search.

The handoff rows $L$ and $M$ attach lift-fiber and homology-core consumers to the same ledger. The structural rows $H,C,P,R$ then transport, replay, source, and locally name the route.

Thus the source theorem is represented as a finite packet. The stated Lean TasteGate obligations are downstream verification requirements for this carrier and do not add fields to the paper-side packet.
\end{proof}

\falsifiablePrediction{For every accepted $\MinimalTriggerOrbitClassificationUp$ packet, componentwise $\hsame$ transport preserves exactly nine displayed normal forms, the quotient-level count $49$, and the codon-level count $294$.}

\independenceWitness{dna-window-six-boundary-tile, minimal-trigger-lift-bundle, minimal-trigger-homology-core, window-coverage-trigger-algebra: $\MinimalTriggerOrbitClassificationUp$ is not bijective to any listed sibling because it jointly carries normal-form rows, defect rows, quotient-count rows, codon-count rows, lift and homology handoffs, transport, replay, provenance, and local naming.}

\closureat{MinimalTriggerOrbitClassificationUp}{seedStr}

\begin{closurestatus}{\MinimalTriggerOrbitClassificationUp}
  \constructivestory{A $\MinimalTriggerOrbitClassificationUp$ packet is generated from a DnaWindowSixBoundaryTile source row, nine normal-form rows, defect ledgers, quotient-count and codon-count rows, MinimalTriggerLiftBundle and MinimalTriggerHomologyCore handoff rows, WindowCoverageTriggerAlgebra provenance, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:minimal-trigger-orbit-classification-carrier}, \autoref{thm:minimal-trigger-orbit-classification-namecert-obligations}, and \autoref{thm:minimal-trigger-orbit-classification-vision-handoff} seed the finite orbit-classification packet preserving nine normal forms, defect rows, quotient count $49$, and codon count $294$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim biological mechanism, stochastic fitness, quotient codon semantics outside displayed rows, unrestricted orbit enumeration, Lean verification, Nontrivial or FieldFaithful TasteGate instances, or bridge checking.}
  \upgradepath{Obligation closure requires checked source admission, normal-form preservation, defect-ledger preservation, quotient-count preservation, codon-count preservation, lift and homology handoffs, transport replay, provenance, local naming, Nontrivial MinimalTriggerOrbitClassificationUp, and FieldFaithful MinimalTriggerOrbitClassificationUp for BEDC.Derived.MinimalTriggerOrbitClassificationUp.}
\end{closurestatus}
