\chapter{A Concrete Naming Certificate for $\RieszRepresentationFiniteLatticeUp$}
\label{ch:concrete-instances-riesz-representation-finite-lattice-namecert}
\origin{human}

Following Riesz and Markov-Kakutani on positive linear functionals over finite lattice data, the $\RieszRepresentationFiniteLatticeUp$ packet records the BEDC-safe finite representation surface for lattice-positive functionals. It consumes the order rows of \autoref{ch:concrete-instances-poset-namecert}, the lattice rows of \autoref{ch:concrete-instances-lattice-namecert}, the one-sided real boundary of \autoref{ch:concrete-instances-real-namecert}, and the lower and upper real approximation rows of \autoref{ch:concrete-instances-lowerreal-namecert} and \autoref{ch:concrete-instances-upperreal-namecert}. The packet is a finite naming certificate for positive functional handoff; it does not assert sigma-additivity, measure completion, quotient dual equality, choice-selected representing measures, or ambient Banach-space representation.

\begin{definition}[Riesz representation finite lattice carrier]
\label{def:riesz-representation-finite-lattice-carrier}
A $\RieszRepresentationFiniteLatticeUp$ carrier is a finite $\BHist$ packet
$$
R=(L,O,F,A,B,P,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LatticeUp$ row, exposing the finite join, meet, top, bottom, and lattice comparison data used by the representation read.
\item $O$ is the $\PosetUp$ row supporting the order classifier shared by the lattice and positivity checks.
\item $F$ is the $\FunctionalAnalysisUp$-style positive functional row, recording additivity on displayed compatible lattice pieces and positivity on the order-positive cone.
\item $A$ is the one-sided $\RealUp$ boundary row through which the functional values are read.
\item $B$ is the $\LowerRealUp$ and $\UpperRealUp$ bracketing row, storing finite lower and upper cuts that witness the one-sided value interval.
\item $P$ is the $\Pkg$ provenance over $\RieszRepresentationFiniteLatticeUp$, $\LatticeUp$, $\PosetUp$, $\RealUp$, $\LowerRealUp$, $\UpperRealUp$, $\FunctionalAnalysisUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $H$ records componentwise $\hsame$ transport for lattice, order, positive-functional, one-sided real, bracketing, provenance, replay, and naming rows.
\item $C$ records displayed $\Cont$ replay from a positive-functional request through $L,O,F,A,B,P,H$.
\item $N$ is the local $\NameCert_{\RieszRepresentationFiniteLatticeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,O,F,A,B,P,H,C,N$. It has no coordinate for completed measure spaces, quotient dual equality, countable joins, choice-selected representing measures, sigma-additivity, or host functional-analysis completion.
\end{definition}

\begin{theorem}[Riesz representation finite lattice NameCert obligations]
\label{thm:riesz-representation-finite-lattice-namecert-obligations}
For every accepted $\RieszRepresentationFiniteLatticeUp$ carrier
$$
R=(L,O,F,A,B,P,H,C,N),
$$
the local $\NameCert_{\RieszRepresentationFiniteLatticeUp}$ surface consists exactly of finite lattice admission, shared poset classifier transport, positive-functional row exposure, one-sided real value readback, lower and upper real bracketing, provenance, componentwise transport, displayed continuation replay, and local naming through $L,O,F,A,B,P,H,C,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:riesz-representation-finite-lattice-carrier}. The rows $L,O,F,A,B,P,H,C,N$ are the whole accepted packet.

The representation read starts with the lattice and order rows. The positive-functional row $F$ is checked only against the displayed lattice operations and the common order classifier supplied by $O$.

The value side is bounded by $A$ and $B$. The one-sided $\RealUp$ row exposes the value seal, while the $\LowerRealUp$ and $\UpperRealUp$ row records the finite bracketing data used by the consumer.

Finally $P,H,C,N$ source, transport, replay, and name the same route. Since the carrier contains no additional coordinate, measure completion, quotient dual equality, countable joins, selected representing measures, and host completion remain outside the local certificate.
\end{proof}

\begin{theorem}[Riesz representation finite lattice positive-functional handoff]
\label{thm:riesz-representation-finite-lattice-positive-functional-handoff}
Every positive-functional consumer of an accepted $\RieszRepresentationFiniteLatticeUp$ carrier factors through the finite route
$$
\LatticeUp,\ \PosetUp,\ \RealUp,\ \LowerRealUp,\ \UpperRealUp,\ \FunctionalAnalysisUp
$$
together with $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows before it exports a representation token.
\end{theorem}
\begin{proof}
Apply \autoref{thm:riesz-representation-finite-lattice-namecert-obligations}. The theorem exposes the lattice, order, positive-functional, one-sided real, bracketing, transport, replay, provenance, and naming rows as the whole obligation surface.

A downstream consumer can therefore read a representation token only after $L,O,F,A,B$ have been displayed in the same finite packet. The structural rows $P,H,C,N$ preserve that route and do not add a second source of representation data.

No row supplies a completed measure, quotient dual equality, countable lattice operation, selected representing measure, sigma-additivity principle, or host Banach-space representation. The handoff is exactly the finite positive-functional route stated above.
\end{proof}

\closureat{RieszRepresentationFiniteLatticeUp}{seedStr}

\begin{closurestatus}{\RieszRepresentationFiniteLatticeUp}
  \constructivestory{A $\RieszRepresentationFiniteLatticeUp$ packet is generated from finite lattice rows, poset classifier rows, positive-functional rows, one-sided Real rows, lower and upper real bracketing rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riesz-representation-finite-lattice-carrier}, \autoref{thm:riesz-representation-finite-lattice-namecert-obligations}, and \autoref{thm:riesz-representation-finite-lattice-positive-functional-handoff} seed the finite positive-functional representation route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim sigma-additive measure representation, completed measure spaces, quotient dual equality, countable lattice joins, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked finite lattice admission, order-positive functional exposure, one-sided value bracketing, replay, transport, provenance, and local naming for BEDC.Derived.RieszRepresentationFiniteLatticeUp.}
\end{closurestatus}
