\chapter{Cauchy compact extraction NameCert construction}
\label{ch:concrete-instances-cauchy-compact-extraction-namecert}
\origin{human}

Following Bishop and Bridges on compact metric spaces, the $\CauchyCompactUp$ extraction packet records the finite route by which total boundedness and completeness turn regular rational observations into a displayed limit seal. It refines the constructive Cauchy-extraction face of \autoref{ch:concrete-instances-cauchy-compact-namecert}, consumes the regular sequence interface of \autoref{ch:concrete-instances-regseqrat-namecert}, and keeps the dyadic tolerance bookkeeping visible through \autoref{ch:concrete-instances-dyadicratcore-namecert}. The chapter names a finite extraction surface only; it does not assert open-cover compactness, a choice-selected subsequence, or host-level real completeness.

\begin{definition}[Cauchy compact extraction carrier]
\label{def:cauchy-compact-extraction-carrier}
A $\CauchyCompactUp$ extraction carrier is a finite $\BHist$ packet
$$
E=(M,L,T,S,R,D,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\CompactMetricUp$ row, exposing the metric carrier, local classifier, and compact metric provenance consumed by the extraction.
\item $L$ is the $\CompleteMetricUp$ row, exposing the finite limit-admission route for the regular Cauchy input named by the packet.
\item $T$ is the $\TotallyBoundedUp$ row, exposing for each dyadic tolerance request the finite net, mesh ledger, and coverage replay used to choose a bounded search window.
\item $S$ is the $\StreamNameUp$ observation schedule, recording the finite windows of the input stream available before the limit seal is read.
\item $R$ is the $\RegSeqRatUp$ regular rational handoff obtained from the displayed stream windows and the same tolerance ledger.
\item $D$ is the $\DyadicRatCoreUp$ ledger for radii, comparisons, refinements, and tail budgets used by $T$, $S$, and $R$.
\item $A$ is the $\RealUp$-facing extracted seal, reachable only after $M,L,T,S,R,D$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the compact metric row, complete metric row, totally bounded row, stream schedule, regular rational handoff, dyadic ledger, extracted seal, continuation, provenance, and local name.
\item $C$ stores displayed $\Cont$ replay of the route
$$
M,L,T,S,R,D \longmapsto A .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompactUp$, $\CompactMetricUp$, $\CompleteMetricUp$, $\TotallyBoundedUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompactUp}$ extraction row.
\end{enumerate}
The classifier compares accepted extraction packets only through these rows. It has no coordinate for open covers, selected subsequences, quotient streams, ambient choice, or a host real object.
\end{definition}

\begin{theorem}[Cauchy compact extraction NameCert obligations]
\label{thm:cauchy-compact-extraction-namecert-obligations}
For every accepted $\CauchyCompactUp$ extraction carrier $E=(M,L,T,S,R,D,A,H,C,P,N)$, the local $\NameCert_{\CauchyCompactUp}$ extraction surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed eleven-row packet;
\item finite-net visibility, requiring each extraction tolerance read to pass through the displayed $\TotallyBoundedUp$ row $T$ over the same $\CompactMetricUp$ row $M$;
\item regular-window compatibility, requiring the $\StreamNameUp$ windows in $S$ and the $\RegSeqRatUp$ handoff $R$ to use the same dyadic tolerance data $D$;
\item completeness handoff, requiring the extracted seal $A$ to be reached through the $\CompleteMetricUp$ row $L$ after the displayed regular Cauchy route has been admitted;
\item ledger confinement, requiring $H,C,P,N$ to transport, replay, source, and name only the displayed extraction route and to export no open-cover compactness, choice-selected subsequence, quotient stream equality, ambient choice, or host real equality.
\end{enumerate}
\end{theorem}

\begin{proof}
Project the accepted carrier. The packet displays exactly the compact metric row, complete metric row, total-bounded finite-net row, stream schedule, regular rational handoff, dyadic ledger, extracted seal, transport, continuation, provenance, and local naming rows.

Finite-net visibility is read from $T$ over $M$. A tolerance request reaches the extraction only by reading the dyadic budget in $D$ and the finite net supplied by the displayed total-bounded row.

Regular-window compatibility is forced before the completion step. The stream windows in $S$ and the regular rational handoff $R$ share the same dyadic ledger $D$, so the completion row cannot read an unnamed Cauchy input.

Finally $L$ produces the seal $A$ and $H,C,P,N$ preserve that same route. Since the tuple contains no row for open covers, selected subsequences, quotient streams, ambient choice, or a host real object, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy compact extraction completion handoff]
\label{thm:cauchy-compact-extraction-completion-handoff}
Every accepted $\CauchyCompactUp$ extraction carrier hands compact metric data to the L10 completion route through
$$
\CompactMetricUp,\quad
\TotallyBoundedUp,\quad
\StreamNameUp,\quad
\RegSeqRatUp,\quad
\DyadicRatCoreUp,\quad
\CompleteMetricUp,\quad
\RealUp
$$
together with the structural rows $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. Any consumer of the extracted seal must first read the finite net, the stream window, the regular rational handoff, the dyadic ledger, and the complete metric limit route.
\end{theorem}

\begin{proof}
Begin with the compact and total-bounded faces. The row $M$ fixes the metric carrier and classifier, while $T$ supplies the finite net and coverage ledger at the dyadic tolerance recorded in $D$.

Read the input stream next. The row $S$ exposes only finite observation windows, and $R$ repacks those windows with $D$ as the regular rational handoff used by the completion side.

Apply the completeness row last. The row $L$ consumes the displayed regular Cauchy route and produces the seal $A$, whose $\RealUp$ face is downstream from the same packet data.

The transport, continuation, provenance, and local naming rows preserve this dependency order. Thus the handoff exports a finite completion-facing route and no open-cover, choice-selected, quotient, ambient-choice, or host-real escape.
\end{proof}
