\chapter{A Concrete Naming Certificate for $\UniformCauchyEmbeddingUp$}
\label{ch:concrete-instances-uniform-cauchy-embedding-namecert}
\origin{human}

Following Bishop and Bridges on uniformly continuous Cauchy data, the $\UniformCauchyEmbeddingUp$ packet records the finite certificate surface for embedding one displayed Cauchy presentation into another without selecting host limits. It sits between the Cauchy source discipline of \autoref{ch:concrete-instances-cauchy-namecert}, the finite schedule rows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the represented-space carrier boundary of \autoref{ch:concrete-instances-representedspace-namecert}. The packet is an open Real and Completion phase object: it makes uniform Cauchy embeddings available as finite NameCert data while leaving completion, quotient equality, and chosen limits outside the carrier.

\begin{definition}[Uniform Cauchy embedding carrier]
\label{def:uniform-cauchy-embedding-carrier}
A $\UniformCauchyEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
U=(C,S,R,T,E,V,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the source $\CauchyUp$ row, recording the Cauchy admissibility request whose observations are to be embedded.
\item $S$ is the $\StreamNameUp$ schedule row opened by a target tolerance request.
\item $R$ is the $\RegSeqRatUp$ regular-rational readback row attached to the source schedule.
\item $T$ is the target $\StreamNameUp$ schedule row, with its tolerance request bounded by a displayed uniform modulus row.
\item $E$ is the $\RealUp$ terminal seal row reached only after the source Cauchy row, the source schedule, the regular readback, and the target schedule have been displayed.
\item $V$ is the $\RepresentedSpaceUp$ representation row for the source and target observation surfaces.
\item $H$ stores componentwise $\hsame$ transport for $C,S,R,T,E,V,K,P,N$.
\item $K$ stores displayed $\Cont$ replay from a target tolerance request back through the source Cauchy, source schedule, regular readback, target schedule, Real seal, and represented-space rows.
\item $P$ is the $\Pkg$ provenance over $\UniformCauchyEmbeddingUp$, $\CauchyUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RepresentedSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformCauchyEmbeddingUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient Cauchy classes, host real equality, a selected completion point, a global inverse map, countable choice, or a proof that the represented-space target is complete.
\end{definition}

\begin{theorem}[Uniform Cauchy embedding NameCert obligations]
\label{thm:uniform-cauchy-embedding-namecert-obligations}
For every accepted $\UniformCauchyEmbeddingUp$ carrier
$$
U=(C,S,R,T,E,V,H,K,P,N),
$$
the local $\NameCert_{\UniformCauchyEmbeddingUp}$ surface consists exactly of carrier admission for the source Cauchy row, source schedule, regular rational readback, target schedule, terminal Real seal, represented-space row, componentwise transport, continuation replay, provenance, and local naming rows, together with the obligation that every target tolerance request is replayed through $C,S,R,T,E,V,H,K,P,N$ in that order.

No obligation in the packet is discharged by quotient Cauchy classes, host real equality, selected completion points, global inverse data, countable choice, or completeness of the represented-space target.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-cauchy-embedding-carrier}. The tuple displays the Cauchy source, source schedule, regular rational readback, target schedule, Real seal, represented-space, transport, replay, provenance, and naming rows.

The replay order is fixed by the row dependencies. A target tolerance request first opens the source Cauchy row $C$, then the finite schedule row $S$, and then the regular-rational readback row $R$ before the target schedule $T$ can be read.

The terminal rows consume only that displayed source surface. The Real seal $E$ records the target real-name boundary, while $V$ records the represented-space observation surface on both sides of the embedding.

Finally $H,K,P,N$ transport, replay, source, and name only these displayed rows. Since the carrier contains no coordinate for the excluded quotient, host, choice, inverse, completion, or completeness data, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Uniform Cauchy embedding sibling route]
\label{thm:uniform-cauchy-embedding-sibling-route}
Every accepted $\UniformCauchyEmbeddingUp$ packet factors through the finite sibling route
$$
\CauchyUp \longrightarrow \StreamNameUp \longrightarrow \RegSeqRatUp \longrightarrow \StreamNameUp \longrightarrow \RealUp \longrightarrow \RepresentedSpaceUp .
$$
The first $\StreamNameUp$ row schedules source observations, and the second $\StreamNameUp$ row schedules target observations under the displayed uniform replay row. The route exports finite embedding data only; it does not export quotient Cauchy classes, selected representatives, global inverse data, or target completeness.
\end{theorem}
\begin{proof}
Apply the obligations of \autoref{thm:uniform-cauchy-embedding-namecert-obligations}. They require every target tolerance request to pass through the source Cauchy row, source schedule, regular rational readback, target schedule, Real seal, and represented-space row.

The two schedule rows have distinct roles. The source schedule $S$ exposes the observations that can be read from the Cauchy source, while the target schedule $T$ records the target request after the displayed uniform replay has bounded it.

The Real and represented-space rows then seal the route without adding non-displayed structure. Because $H,K,P,N$ only transport, replay, source, and name the same rows, the packet exports the finite sibling route and none of the excluded quotient, representative, inverse, or completeness data.
\end{proof}

\begin{theorem}[Uniform Cauchy embedding open phase use]
\label{thm:uniform-cauchy-embedding-open-phase-use}
In the open Real and Completion phase, a $\UniformCauchyEmbeddingUp$ packet may be used as the finite handoff object from regular Cauchy source data to Real-facing and represented-space-facing consumers. Such a consumer may read the displayed Cauchy, schedule, regular-rational, target-schedule, Real-seal, represented-space, transport, replay, provenance, and naming rows, but it may not infer completion of $\RealUp$, a quotient construction for Cauchy names, a selected limit, or countable-choice data.
\end{theorem}
\begin{proof}
The handoff object is the carrier of \autoref{def:uniform-cauchy-embedding-carrier}. Its rows expose exactly the source Cauchy request, the two finite schedules, the regular rational readback, the Real seal, the represented-space surface, and the structural transport, replay, provenance, and naming data.

The open phase use reads this finite surface as an interface for later Real and Completion obligations. It can therefore pass uniform Cauchy embedding evidence downstream without changing the carrier into a completion theorem.

The exclusions follow from absence of coordinates. Since the carrier contains no quotient construction, selected limit, completeness proof, or countable-choice row, no open phase consumer obtains those data from the $\UniformCauchyEmbeddingUp$ NameCert.
\end{proof}

\begin{closurestatus}{\UniformCauchyEmbeddingUp}
  \constructivestory{A $\UniformCauchyEmbeddingUp$ packet is generated from a source Cauchy row, source schedule, regular rational readback, target schedule, terminal Real seal, represented-space row, componentwise transport, displayed continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-embedding-carrier}, \autoref{thm:uniform-cauchy-embedding-namecert-obligations}, \autoref{thm:uniform-cauchy-embedding-sibling-route}, and \autoref{thm:uniform-cauchy-embedding-open-phase-use} seed the finite uniform Cauchy embedding interface for the open Real and Completion phase.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, quotient Cauchy equality, selected completion points, global inverse data, countable choice, $\RealUp$ completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform replay non-escape, sibling route coverage, and open phase use for the same packet.}
\end{closurestatus}
