\chapter{A Concrete Naming Certificate for $\MetricBaireSpaceUp$}
\label{ch:concrete-instances-metric-baire-space-namecert}
\origin{human}

Following Baire and Oxtoby, the $\MetricBaireSpaceUp$ packet records the
complete separable metric route through which a Baire-space consumer reads
finite names. It sits after the metric carrier of
\autoref{ch:concrete-instances-metric-space-namecert}, the completion service
of \autoref{ch:concrete-instances-completemetric-namecert}, the dense schedule
of \autoref{ch:concrete-instances-separablemetric-namecert}, the finite
windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular
rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and
the prefix surface of \autoref{ch:concrete-instances-bairespace-namecert}.
The packet binds those rows as one complete-separable Baire naming surface
without adding countable choice, a host topology, quotient point equality, or
an external completion coordinate.

\begin{definition}[Metric Baire-space carrier]
\label{def:metric-baire-space-carrier}
A $\MetricBaireSpaceUp$ carrier is a finite $\BHist$ packet
$$
P=(M,K,D,S,R,B,H,C,P_0,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ source row carrying the admitted point
history, metric readbacks, distance classifier, and local metric naming.
\item $K$ is the $\CompleteMetricUp$ row over the same metric carrier,
displaying the Cauchy-window and limit-service route.
\item $D$ is the $\SeparableMetricUp$ row exposing a countable dense schedule
as finite name data rather than as a choice function.
\item $S$ is the $\StreamNameUp$ row scheduling finite inspections of dense
names, Baire prefixes, metric balls, and Cauchy-window requests.
\item $R$ is the $\RegSeqRatUp$ row that reads rational windows for centers,
radii, tolerances, and regular Cauchy approximants.
\item $B$ is the $\BaireSpaceUp$ ledger row recording finite-prefix and
cylinder reads consumed by the Baire-space side of the packet.
\item $H$ records componentwise $\hsame$ transport for $M,K,D,S,R,B$ and the
local certificate rows.
\item $C$ records displayed $\Cont$ replay from a metric-ball, dense-name,
Cauchy-window, or Baire-prefix request through the visible rows.
\item $P_0$ is the $\Pkg$ provenance over $\MetricBaireSpaceUp$,
$\MetricSpaceUp$, $\CompleteMetricUp$, $\SeparableMetricUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\BaireSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricBaireSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only after transporting the metric,
complete-metric, separable-metric, stream, regular-readback, and Baire-prefix
rows to one common surface. It has no coordinate for a selected dense
sequence, a host completion, arbitrary open-cover semantics, quotient point
equality, or a generic-point selector.
\end{definition}

\begin{theorem}[Metric Baire-space NameCert obligations]
\label{thm:metric-baire-space-namecert-obligations}
For every accepted $\MetricBaireSpaceUp$ carrier
$P=(M,K,D,S,R,B,H,C,P_0,N)$, the local
$\NameCert_{\MetricBaireSpaceUp}$ surface consists exactly of carrier
admission for the metric, complete-metric, separable-metric, stream,
regular-readback, Baire-prefix, transport, replay, provenance, and local-name
rows; classifier transport to a common metric carrier before any completion,
density, or Baire-prefix row is consumed; observation-ledger exactness through
$S,R,B$; stability under the componentwise transports in $H$; displayed
$\Cont$ replay through $C$; and provenance plus local naming through $P_0,N$.
No naming obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metric-baire-space-carrier}. The rows
$M,K,D,S,R,B$ are the analytic surfaces, and $H,C,P_0,N$ are the structural
transport, replay, provenance, and naming surfaces.

The classifier route begins at $M$. The complete-metric row $K$, separable
row $D$, and Baire-prefix row $B$ are read only after the componentwise
transport row has placed them over the same metric carrier.

The finite observation route is exhausted by $S,R,B$. Dense-name requests,
Cauchy-window requests, metric-ball checks, and Baire-prefix reads all pass
through the stream schedule and regular rational readback before any consumer
can use them.

Finally replay through $C$ and attach $P_0,N$. Since the carrier contains no
coordinate for a selected dense sequence, host completion, arbitrary
open-cover object, quotient point equality, or generic-point selector, the
listed rows exhaust the local NameCert obligations.
\end{proof}

\closureat{MetricBaireSpaceUp}{seedStr}

\begin{closurestatus}{\MetricBaireSpaceUp}
  \constructivestory{A $\MetricBaireSpaceUp$ packet is generated from a MetricSpace source row, CompleteMetric handoff row, SeparableMetric dense schedule, StreamName finite windows, RegSeqRat readback, BaireSpace prefix ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-baire-space-carrier} and \autoref{thm:metric-baire-space-namecert-obligations} seed the complete-separable metric Baire naming surface consumed by downstream Polish and Baire chapters.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected dense sequences, host completions, arbitrary open-cover semantics, quotient point equality, generic-point selectors, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, common metric transport, completion service, dense schedule, StreamName windows, RegSeqRat readback, Baire-prefix ledger exactness, replay, provenance, and local naming for BEDC.Derived.MetricBaireSpaceUp.}
\end{closurestatus}
