\chapter{A Concrete Naming Certificate for $\OlivierTheoremUp$}
\label{ch:concrete-instances-olivier-theorem-namecert}
\origin{human}

Following Olivier's theorem for positive convergent series, the $\OlivierTheoremUp$ packet records the finite positive-term tail evidence by which a Real-facing series consumer may read vanishing terms without importing a host completeness theorem. It sits after the summable-tail modulus of \autoref{ch:concrete-instances-summable-tail-modulus-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a constructive tail handoff for positive series; it exports no selected sum, quotient series equality, choice, host real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Olivier theorem carrier]
\label{def:olivier-theorem-carrier}
An $\OlivierTheoremUp$ carrier is a finite $\BHist$ packet
$$
O=(A,T,M,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the positive-term series row, exposing only the inspected nonnegative term windows and finite partial-sum comparison windows used by the current request.
\item $T$ is the tail-window row, naming the finite interval of terms whose smallness is to be served.
\item $M$ is the $\SummableTailModulusUp$ row, assigning the requested positive-term tail window to a displayed summable-tail modulus before any regular rational readback is available.
\item $R$ is the $\RegSeqRatUp$ handoff row reached only after $A,T,M$ have displayed the finite tail evidence.
\item $E$ is the terminal $\RealUp$ seal row reached only after the regular rational handoff and the summable-tail route have been replayed.
\item $H$ records componentwise $\hsame$ transport for the positive-term, tail-window, modulus, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a positive-series tail request through $A,T,M,R,E$.
\item $P$ is the $\Pkg$ provenance over $\OlivierTheoremUp$, $\SummableTailModulusUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\OlivierTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for selected sums, quotient series equality, choice, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Olivier theorem NameCert obligations]
\label{thm:olivier-theorem-namecert-obligations}
For every accepted $\OlivierTheoremUp$ carrier $O=(A,T,M,R,E,H,C,P,N)$, the local $\NameCert_{\OlivierTheoremUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the positive-term series row, finite tail-window row, summable-tail modulus row, regular rational handoff, Real seal, transport, replay, provenance, and local naming row;
\item positivity-window exposure, requiring $A$ to supply the only term-sign and finite partial-sum data used by the tail request;
\item tail-window service, requiring $T$ to name the inspected positive-term tail window before any downstream read can ask for vanishing terms;
\item modulus handoff, requiring $T$ to pass through the $\SummableTailModulusUp$ row $M$ before the $\RegSeqRatUp$ handoff $R$ is available;
\item non-escape, requiring every terminal $\RealUp$ read to pass through $A,T,M,R,H,C,P,N$ and excluding selected sums, quotient series equality, choice, host real equality, and ambient $\RealUp$ completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:olivier-theorem-carrier}. The visible inventory is $A,T,M,R,E,H,C,P,N$, so the certificate has no detached row for a selected sum, quotient series equality, choice, host real equality, or ambient completeness theorem.

The positive-term and finite-window data are read before any Real-facing seal is available. The row $A$ supplies the inspected positive term and partial-sum comparison windows, while $T$ identifies the concrete tail window served by the request.

The tail window then passes through $M$. Thus finite positive-term tail evidence is converted into a displayed $\SummableTailModulusUp$ service before any $\RegSeqRatUp$ readback can occur.

Finally $R,E,H,C,P,N$ supply regular readback, terminal sealing, transport, replay, provenance, and local naming for the same route. Since the excluded analytic objects are not carrier coordinates, they cannot be exported by the local certificate.
\end{proof}

\begin{theorem}[Olivier theorem tail handoff]
\label{thm:olivier-theorem-tail-handoff}
Every Real-facing read of an accepted $\OlivierTheoremUp$ carrier factors finite positive-term tail windows through the ordered route
$$
\OlivierTheoremUp \longmapsto \SummableTailModulusUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Consequently a consumer may use Olivier-style vanishing-term evidence only after the displayed summable-tail modulus row has served the finite tail window. It receives no selected sum, quotient series equality, choice, host real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $O=(A,T,M,R,E,H,C,P,N)$ and a Real-facing request for positive-series tail evidence. The only source row is $A$, and the only finite tail-window row is $T$.

The handoff is then forced through $M$. This makes the Olivier-style conclusion a finite modulus-served tail read, not a hidden selection of a sum or an equality of quotient series.

Only after $M$ appears may the route enter $R$ and then the terminal $\RealUp$ seal $E$. The rows $H,C,P,N$ preserve the same displayed route under transport, replay it as continuation data, record provenance, and name it locally, so no excluded completeness or choice principle is introduced downstream.
\end{proof}

\falsifiablePrediction{Every accepted $\OlivierTheoremUp$ Real-facing tail read factors through positive-term windows, a finite tail-window row, a SummableTailModulus row, RegSeqRat readback, Real sealing, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{summable-tail-modulus, regseqrat, real: $\OlivierTheoremUp$ is not bijective to any listed sibling because it binds positive-term series windows, finite tail evidence, summable-tail modulus service, regular rational readback, terminal Real sealing, transport, replay, provenance, and local naming as one certificate.}

\closureat{OlivierTheoremUp}{seedStr}

\begin{closurestatus}{\OlivierTheoremUp}
  \constructivestory{An $\OlivierTheoremUp$ packet is generated from positive-term series windows, finite tail-window evidence, a SummableTailModulus row, RegSeqRat readback, Real sealing, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:olivier-theorem-carrier}, \autoref{thm:olivier-theorem-namecert-obligations}, and \autoref{thm:olivier-theorem-tail-handoff} seed the finite positive-series tail route over displayed summable-tail modulus, $\RegSeqRatUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected sums, quotient series equality, choice, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, positivity-window exposure, tail-window service, modulus handoff, regular rational readback, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.OlivierTheoremUp.}
\end{closurestatus}
