\chapter{A Concrete Naming Certificate for $\LagrangeInterpolationUp$}
\label{ch:concrete-instances-lagrange-interpolation-namecert}
\origin{human}

Following Lagrange's interpolation formula, the $\LagrangeInterpolationUp$
packet records the finite route from distinct interpolation nodes and displayed
values to a polynomial whose evaluations match those values. It consumes the
polynomial coefficient-list surface of
\autoref{ch:concrete-instances-polynomial-namecert}, the matrix-style finite
table discipline of \autoref{ch:concrete-instances-matrix-namecert}, and the
field and rational arithmetic boundaries of
\autoref{ch:concrete-instances-field-namecert} and
\autoref{ch:concrete-instances-rat-namecert}. Its BEDC carrier is a finite
$\BHist$ ledger: it names nodes, values, basis-polynomial construction,
evaluation rows, uniqueness rows, $\hsame$ transport, $\Cont$ replay, $\Pkg$
provenance, and a local $\NameCert$ row. It is not a host interpolation
theorem, a quotient polynomial equality, or an ambient field-completion
principle.

The history rows are read as ordinary BEDC certificate data in the sense of
\autoref{ch:concrete-instances-b-hist-hendeca-tuple-namecert} and the typed
naming discipline of \autoref{ch:core-typed-naming-certificates}. The classical
formula appears only through finite arithmetic ledgers; every consumer sees the
displayed nodes, denominators, coefficient rows, and evaluation routes before
it can use the interpolating polynomial.

\begin{definition}[Lagrange interpolation carrier]
\label{def:lagrange-interpolation-carrier}
A $\LagrangeInterpolationUp$ source is a finite $\mathsf{BHist}$ packet
$$
L=(N,V,D,B,E,U,H,C,P,Q)
$$
with the following visible rows:
\begin{enumerate}
\item $N$ is a nonempty finite node row, with an index list and a displayed
pairwise-distinctness ledger for the nodes.
\item $V$ is the value row assigning one carried scalar value to each node of
$N$.
\item $D$ is the denominator ledger for the factors $x_i-x_j$ with
$i\ne j$, routed through $\FieldUp$ inverse rows and the rational arithmetic
surface when the nodes are rational.
\item $B$ is the basis-polynomial row, displaying the finite products
$$
\ell_i(X)=\prod_{j\ne i}\frac{X-x_j}{x_i-x_j}
$$
as normalized $\PolynomialUp$ coefficient lists.
\item $E$ is the evaluation row, recording that each $\ell_i$ evaluates to the
Kronecker pattern on the displayed node list.
\item $U$ is the polynomial assembly and uniqueness row: it records the finite
sum $\sum_i V_i\ell_i$ and the finite comparison showing that any other
polynomial of degree below the displayed node count with the same evaluations
has the same normalized coefficient list.
\item $H$ records componentwise $\hsame$ transport for the node, value,
denominator, basis, evaluation, uniqueness, replay, provenance, and local-name
rows.
\item $C$ records the $\Cont$ routes that replay denominator formation,
basis-polynomial multiplication, polynomial evaluation, and uniqueness
comparison from the same displayed finite packet.
\item $P$ is the $\Pkg$ provenance over $\LagrangeInterpolationUp$,
$\PolynomialUp$, $\MatrixUp$, $\FieldUp$, $\RatUp$, $\BHist$, $\hsame$,
$\Cont$, and $\NameCert$.
\item $Q$ is the local $\NameCert_{\LagrangeInterpolationUp}$ row.
\end{enumerate}
The carrier predicate is
$\mathsf{LagrangeInterpolationLedger}(N,V,D,B,E,U,H,C,P,Q)$. Two accepted
packets classify together exactly when the ten displayed rows are transported
by $H$ and replay through the same routes named by $C$ and $P$.
\end{definition}

\begin{theorem}[Lagrange interpolation NameCert obligations]
\label{thm:lagrange-interpolation-namecert-obligations}
For an accepted $\LagrangeInterpolationUp$ packet
$L=(N,V,D,B,E,U,H,C,P,Q)$, the local
$\NameCert_{\LagrangeInterpolationUp}$ obligation surface consists exactly of
the finite carrier and classifier rows of
\autoref{def:lagrange-interpolation-carrier}, the denominator nonzero rows
$D$, the basis-polynomial construction rows $B$, the evaluation rows $E$, the
assembly and uniqueness rows $U$, the componentwise $\hsame$ transport $H$, the
displayed $\Cont$ replay $C$, the $\Pkg$ provenance $P$, and the local naming
row $Q$. No additional host polynomial function, determinant inverse, quotient
equality of polynomials, infinite node family, or completion datum is exported.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:lagrange-interpolation-carrier}. The rows
$N$ and $V$ supply the finite interpolation table, while $D$ records exactly
the nonzero denominator data forced by distinct nodes.

The basis and evaluation content is held by $B$ and $E$. These rows are typed
over the same polynomial coefficient-list surface and the same scalar
arithmetic provenance, so their comparisons do not introduce a second carrier.

The row $U$ is the only place where the assembled polynomial and the
degree-bounded uniqueness comparison are visible. The remaining rows $H,C,P,Q$
transport, replay, source, and name the displayed packet. Since no further
coordinate is present, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Lagrange polynomial evaluation route]
\label{thm:lagrange-interpolation-polynomial-evaluation-route}
Every evaluation read exported by an accepted $\LagrangeInterpolationUp$
packet factors through the same finite route
$$
N,V,D \longmapsto B \longmapsto E \longmapsto U \longmapsto Q .
$$
The route first verifies pairwise-distinct nodes and denominator rows, then
builds normalized basis polynomials in $\PolynomialUp$, evaluates those basis
polynomials at the displayed nodes, assembles the interpolating polynomial, and
finally exposes the local $\NameCert_{\LagrangeInterpolationUp}$ row. A
consumer cannot bypass this route by appealing to an ambient polynomial
function, a determinant computation over an unstated matrix, or an external
field-completion argument.
\end{theorem}
\begin{proof}
Start with an accepted packet
$L=(N,V,D,B,E,U,H,C,P,Q)$. The denominator ledger $D$ is downstream of the
node row $N$ and upstream of the basis row $B$, so each basis-polynomial read
has already passed through the displayed distinctness and inverse witnesses.

Next, $E$ evaluates the basis rows of $B$ at the same finite node list. The
route is replayed by $C$ and transported by $H$, hence a transported packet
keeps the same node, value, denominator, basis, and evaluation sequence.

Finally, $U$ assembles the finite linear combination and records the
degree-bounded uniqueness comparison before $Q$ names the packet. Thus every
polynomial-evaluation read available from the local certificate follows the
displayed finite route and has no coordinate from which a bypassing host
argument could be read.
\end{proof}

\falsifiablePrediction{Every accepted $\LagrangeInterpolationUp$ read that
claims an interpolating polynomial factors through finite node rows, value rows,
denominator ledgers, normalized $\PolynomialUp$ basis rows, evaluation rows,
uniqueness rows, componentwise $\hsame$ transport, displayed $\Cont$ replay,
$\Pkg$ provenance, and the local $\NameCert$ row.}

\closureat{LagrangeInterpolationUp}{seedStr}

\begin{closurestatus}{\LagrangeInterpolationUp}
  \constructivestory{A $\LagrangeInterpolationUp$ packet is generated from finite node rows, value rows, denominator ledgers, basis-polynomial rows, evaluation rows, assembly and uniqueness rows, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lagrange-interpolation-carrier}, \autoref{thm:lagrange-interpolation-namecert-obligations}, and \autoref{thm:lagrange-interpolation-polynomial-evaluation-route} seed the finite interpolation route over polynomial, matrix, field, rational, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host interpolation theorems, quotient polynomial equality, determinant inverses outside the displayed rows, infinite node families, field-completion data, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, denominator nonzero rows, basis-polynomial construction, evaluation rows, assembly and uniqueness rows, and transport/provenance/name exhaustion for BEDC.Derived.LagrangeInterpolationUp.}
\end{closurestatus}
