\chapter{A Concrete Naming Certificate for $\BesovSpaceUp$}
\label{ch:concrete-instances-besov-space-namecert}
\origin{human}

Following Besov and Triebel's constructive regularity scale, the $\BesovSpaceUp$ packet records a finite smoothness-measurement surface between Sobolev weak-gradient data and Holder power-law control. It sits after the Sobolev ledger of \autoref{ch:concrete-instances-sobolev-namecert}, the Holder continuity route of \autoref{ch:concrete-instances-holder-continuity-namecert}, the weak-derivative handoff of \autoref{ch:concrete-instances-weak-derivative-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet names only displayed smoothness windows, dyadic scale budgets, weak-action rows, real readback, transport, replay, provenance, and local naming; it does not import open-cover compactness, quotient function spaces, selected representatives, or ambient $\RealUp$ completeness.

\begin{definition}[Besov space carrier]
\label{def:besov-space-carrier}
A $\BesovSpaceUp$ carrier is a finite $\BHist$ packet
$$
B=(S,Hd,W,R,Q,D,E,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SobolevUp$ source row, recording the weak-gradient and integrability ledger consumed by the regularity request.
\item $Hd$ is the $\HolderContinuityUp$ boundary row, recording the visible power-law modulus data used when the Besov packet exposes pointwise smoothness control.
\item $W$ is the $\WeakDerivativeUp$ action row, naming the finite test probes and derivative observations inspected by the scale request.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational magnitude data attached to the selected smoothness windows.
\item $Q$ is the $\StreamNameUp$ finite-window schedule, selecting the scale windows, test probes, and comparison requests visible to this packet.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic scale, radius, and comparison budget attached to the same windows.
\item $E$ is the terminal $\RealUp$ seal row reached only after $S,Hd,W,R,Q,D$ have been displayed.
\item $T$ stores componentwise $\hsame$ transport for the regularity, window, tolerance, real-seal, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a Besov regularity request through the Sobolev, Holder, weak-derivative, regular-rational, stream, dyadic, and real-seal rows.
\item $P$ is the $\Pkg$ provenance over $\BesovSpaceUp$, $\SobolevUp$, $\HolderContinuityUp$, $\WeakDerivativeUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BesovSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $S,Hd,W,R,Q,D,E,T,C,P,N$. It has no coordinate for an open-cover compactness theorem, quotient equality of function spaces, selected representatives, a completed smoothness scale, host distribution equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Besov space NameCert obligations]
\label{thm:besov-space-namecert-obligations}
For every accepted $\BesovSpaceUp$ carrier $B=(S,Hd,W,R,Q,D,E,T,C,P,N)$, the local $\NameCert_{\BesovSpaceUp}$ surface consists exactly of carrier admission for the displayed Sobolev row, Holder row, weak-derivative action row, regular rational readback row, stream-window schedule, dyadic scale ledger, terminal real seal, componentwise transport, displayed replay, provenance, and local naming rows. Every regularity, PDE, interpolation, or trace-facing consumer of the packet must read through those rows before it cites the Besov smoothness boundary.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:besov-space-carrier}. The analytic rows are $S,Hd,W,R,Q,D,E$, and the structural rows are $T,C,P,N$.

The Sobolev, Holder, and weak-derivative rows have distinct roles. The Sobolev row supplies the weak-gradient and integrability ledger, the Holder row supplies the visible power-law boundary, and the weak-derivative row supplies the finite test-action observations.

The scale and readback rows then fix the measurable part of the packet. The stream schedule $Q$ opens the finite windows, the dyadic ledger $D$ records the scale and comparison budget, the regular rational row $R$ reads the displayed magnitudes, and the real seal $E$ is reached only after those rows have been inspected.

Finally $T,C,P,N$ transport, replay, source, and name the same finite route. Since no open-cover compactness theorem, quotient function-space equality, selected representative, completed smoothness scale, host distribution equality, countable choice, or ambient completeness coordinate appears in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Besov space L10 handoff]
\label{thm:besov-space-l10-handoff}
Every L10 regularity consumer of an accepted $\BesovSpaceUp$ carrier factors through the finite route
$$
\SobolevUp \longrightarrow \WeakDerivativeUp \longrightarrow \HolderContinuityUp \longrightarrow \StreamNameUp \longrightarrow \DyadicRatCoreUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp .
$$
The handoff exports displayed smoothness-window data, dyadic scale control, regular rational readback, terminal real seals, componentwise transport, continuation replay, provenance, and local naming. It exports no open-cover compactness theorem, quotient function space, selected representative, host equality of functions or distributions, countable-choice row, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:besov-space-namecert-obligations}. They require every accepted regularity read to pass through the Sobolev, Holder, and weak-derivative rows before any downstream smoothness boundary is cited.

Next read the finite scale data. The stream schedule $Q$ chooses the visible windows, while the dyadic ledger $D$ attaches the scale and tolerance budget to those same windows.

The regular rational readback row $R$ and terminal real seal $E$ then report the displayed magnitude data. The structural rows $T,C,P,N$ preserve the route under transport, replay, provenance, and local naming.

Thus an L10 consumer receives exactly the displayed chain from Sobolev and weak-derivative evidence through Holder, stream, dyadic, regular-rational, and real-seal rows. The excluded compactness, quotient, representative-selection, host-equality, choice, and ambient-completeness objects have no carrier coordinate and cannot be exported by the packet.
\end{proof}

\falsifiablePrediction{Every accepted $\BesovSpaceUp$ regularity consumer must read Sobolev, HolderContinuity, WeakDerivative, StreamName, DyadicRatCore, RegSeqRat, Real, hsame, Cont, Pkg, and local NameCert rows before citing the Besov smoothness boundary.}

\independenceWitness{sobolev, holder-continuity, weak-derivative, real, streamname, regseqrat, dyadicratcore: $\BesovSpaceUp$ is not bijective to any listed sibling because it jointly carries smoothness-source rows, pointwise power-law boundary data, weak-action observations, finite windows, dyadic scale budgets, regular rational readback, real seals, transport, replay, provenance, and local naming.}

\closureat{BesovSpaceUp}{seedStr}
\begin{closurestatus}{\BesovSpaceUp}
  \constructivestory{A $\BesovSpaceUp$ packet is generated from Sobolev, HolderContinuity, WeakDerivative, RegSeqRat, StreamName, DyadicRatCore, Real, componentwise hsame, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:besov-space-carrier}, \autoref{thm:besov-space-namecert-obligations}, and \autoref{thm:besov-space-l10-handoff} seed the finite constructive regularity-space route over Sobolev, HolderContinuity, WeakDerivative, Real, StreamName, RegSeqRat, DyadicRatCore, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, open-cover compactness, quotient function spaces, selected representatives, host equality of functions or distributions, countable choice, ambient Real completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, smoothness-window exactness, dyadic-scale ledger stability, regular rational readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BesovSpaceUp.}
\end{closurestatus}
