\chapter{A Concrete Naming Certificate for $\RegularCauchyDiagonalSealUp$}
\label{ch:concrete-instances-regular-cauchy-diagonal-seal-namecert}
\origin{human}

Following Bishop and Bridges regular Cauchy completeness, the $\RegularCauchyDiagonalSealUp$ packet records the finite-window handoff from local regular Cauchy sections to a terminal $\RealUp$ seal. It consumes the stream-window carrier of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational classifier of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}. The packet names the diagonal gluing route; it is not a quotient of streams, a selected representative, a metric completion object, a countable-choice schedule, or an ambient theorem that all Cauchy data already have host limits.

\begin{definition}[Regular Cauchy diagonal seal carrier]
\label{def:real-completeness-regular-cauchy-diagonal-seal-carrier}
A $\RegularCauchyDiagonalSealUp$ carrier is a finite $\BHist$ packet
$$
D=(F,S,E,R,L,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite section family, listing the local regular-Cauchy windows admitted for one completion request.
\item $S$ is the $\StreamNameUp$ window family shared by the local sections and the diagonal readback.
\item $E$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the finite precision rows used to compare the local windows.
\item $R$ is the $\RegSeqRatUp$ classifier and regularity ledger, including the accepted local readback rows and the displayed regularity witnesses.
\item $L$ is the local $\RealUp$ seal row for each admitted section before diagonal gluing.
\item $G$ is the diagonal-gluing ledger. It records the finite refinement route that sends the local $F,S,E,R,L$ rows to one terminal diagonal window.
\item $H$ records componentwise $\hsame$ transport for the finite section family, StreamName windows, dyadic tolerance rows, RegSeqRat classifier and regularity rows, local Real seals, diagonal-gluing ledger, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
F,S,E,R,L \longmapsto G \longmapsto H .
$$
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyDiagonalSealUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyDiagonalSealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,S,E,R,L,G,H,C,P,N$. It has no coordinate for quotient stream equality, a selected representative, a countable-choice schedule, a host completion point, metric-completeness data, or an ambient $\RealUp$ completeness principle.
\end{definition}

\begin{theorem}[Regular Cauchy diagonal seal NameCert obligations]
\label{thm:real-completeness-regular-cauchy-diagonal-seal-obligations}
For every accepted $\RegularCauchyDiagonalSealUp$ carrier
$$
D=(F,S,E,R,L,G,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyDiagonalSealUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item finite-section admission for $F$, requiring every local section to be displayed before the diagonal route is read;
\item StreamName and dyadic tolerance compatibility for $S,E$, requiring all local windows to share the recorded precision ledger;
\item RegSeqRat classifier and regularity exposure for $R$, requiring local readbacks and regularity witnesses to be displayed as finite rows;
\item local Real seal exposure for $L$, requiring each section's terminal read to pass through the same RegSeqRat and tolerance rows;
\item diagonal gluing exactness for $G$, requiring the terminal diagonal window to be assembled from the displayed local rows only;
\item transport, replay, provenance, and local naming through $H,C,P,N$, preserving exactly the same diagonal-seal packet.
\end{enumerate}
No regular Cauchy diagonal seal obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:real-completeness-regular-cauchy-diagonal-seal-carrier}. The finite section family $F$ supplies the only local regular-Cauchy windows available to the packet.

The StreamName and dyadic rows $S,E$ place those sections over one displayed precision interface. The RegSeqRat row $R$ then records the classifier and regularity witnesses used by each local readback, and the Real row $L$ records the local terminal seals before they are glued.

The diagonal-gluing ledger $G$ is the only row that assembles a terminal diagonal window from those local data. It therefore carries the exactness obligation for the finite-window handoff and cannot be replaced by a quotient stream, selected representative, or host completion point.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed tuple. Since no further coordinate is present, the six listed rows exhaust the local naming obligations.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal seal vision handoff]
\label{thm:real-completeness-regular-cauchy-diagonal-seal-vision-handoff}
The regular Cauchy diagonal seal realizes the finite-window route from local regular sections to the terminal $\RealUp$ seal: any read of the terminal seal from a section in $F$ factors through the common $\StreamNameUp$ window family, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ classifier and regularity rows, local $\RealUp$ seal rows, and diagonal-gluing ledger of \autoref{def:real-completeness-regular-cauchy-diagonal-seal-carrier}.
\end{theorem}
\begin{proof}
Start with a terminal seal read from a local section. By carrier admission, the section appears in $F$ and its stream window and tolerance rows are displayed in $S$ and $E$.

The RegSeqRat classifier and regularity ledger $R$ places the local readback inside the regular rational sequence surface, while the row $L$ records the section's local $\RealUp$ seal. These rows are the only available route from the local section to a terminal real-facing read.

Apply the diagonal-gluing ledger $G$. It sends the local rows through the shared finite window into the terminal diagonal seal and leaves no coordinate for quotient stream equality, selected representatives, countable-choice schedules, metric-completeness data, completion points, or ambient Real completeness. Thus the vision-side regular Cauchy handoff is represented by the displayed NameCert packet.
\end{proof}

\closureat{RegularCauchyDiagonalSealUp}{seedStr}

\begin{closurestatus}{\RegularCauchyDiagonalSealUp}
  \constructivestory{A $\RegularCauchyDiagonalSealUp$ packet is generated from a finite section family, StreamNameUp window family, DyadicRatCoreUp tolerance ledger, RegSeqRatUp classifier and regularity ledger, local RealUp seal rows, diagonal-gluing ledger, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-completeness-regular-cauchy-diagonal-seal-carrier}, \autoref{thm:real-completeness-regular-cauchy-diagonal-seal-obligations}, and \autoref{thm:real-completeness-regular-cauchy-diagonal-seal-vision-handoff} seed the finite regular-Cauchy diagonal route from local section windows to a terminal RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected representatives, countable-choice schedules, metric-completeness data, completion points, ambient RealUp completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked finite-section admission, StreamName and dyadic tolerance compatibility, RegSeqRat classifier exposure, local Real seal exposure, diagonal gluing exactness, and transport/provenance/name exhaustion for BEDC.Derived.RegularCauchyDiagonalSealUp.}
\end{closurestatus}
