\chapter{Modulus of Total Boundedness NameCert Construction}
\label{ch:concrete-instances-modulus-of-total-boundedness-namecert}
\origin{human}

Following Bishop and Bridges constructive metric analysis, the $\ModulusOfTotalBoundednessUp$ packet records the explicit schedule form of total boundedness: a positive dyadic tolerance request is answered by a finite epsilon-net row together with the finite ledger proving coverage at that tolerance. The packet sits between the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation interface of \autoref{ch:concrete-instances-streamname-namecert}, the total-bounded finite-net carrier of \autoref{ch:concrete-instances-totallybounded-namecert}, and the compact-metric consumer of \autoref{ch:concrete-instances-compactmetric-namecert}. It names the schedule consumed by compact and continuous routes without invoking open-cover compactness, selected representatives, countable choice, or ambient completeness.

\falsifiablePrediction{A compact-metric or continuous-route certificate that consumes a total-boundedness claim without displaying the dyadic tolerance request and its finite net schedule refutes $\ModulusOfTotalBoundednessUp$, because the packet's carrier has no hidden open-cover compactness or selected-net coordinate.}

\independenceWitness{$\mathrm{totally\_bounded}$, $\mathrm{compact\_metric}$, $\mathrm{stream\_name}$, $\mathrm{dyadic\_rat\_core}$: none is bijective to $\ModulusOfTotalBoundednessUp$ because the modulus packet jointly records the tolerance request, schedule index, finite center bundle, coverage ledger, metric comparison rows, transport, replay, provenance, and local naming as one displayed schedule surface.}

\begin{definition}[Modulus of total boundedness carrier]
\label{def:modulus-of-total-boundedness-carrier}
A $\ModulusOfTotalBoundednessUp$ carrier is a finite $\BHist$ packet
$$
M=(X,D,S,T,K,L,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $X$ is the $\MetricSpaceUp$ source row carrying the point classifier and distance comparison ledger.
\item $D$ is the $\DyadicRatCoreUp$ positive tolerance request.
\item $S$ is the $\StreamNameUp$ finite observation window naming the displayed tolerance and center schedule.
\item $T$ is the $\TotallyBoundedUp$ finite-net source row.
\item $K$ is the finite $\ProbeBundle$ of center histories selected by the schedule for the tolerance row $D$.
\item $L$ is the coverage ledger, recording membership, center-carrier rows, distance witnesses, and dyadic comparison rows for the centers in $K$.
\item $H$ records componentwise $\hsame$ transport for metric, tolerance, window, total-bounded, center-bundle, coverage, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for compact or continuous consumers through $X,D,S,T,K,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\ModulusOfTotalBoundednessUp$, $\MetricSpaceUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ModulusOfTotalBoundednessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,D,S,T,K,L,H,C,P,N$. It has no coordinate for an open-cover subcover, a host-selected finite set, a quotient completion, a global compactness theorem, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[Modulus of total boundedness NameCert obligations]
\label{thm:modulus-of-total-boundedness-namecert-obligations}
For every accepted $\ModulusOfTotalBoundednessUp$ carrier $M=(X,D,S,T,K,L,H,C,P,N)$, the local $\NameCert_{\ModulusOfTotalBoundednessUp}$ surface consists exactly of carrier admission, metric-source exposure, dyadic tolerance exposure, finite-window exposure, total-bounded source exposure, finite center-bundle exposure, coverage-ledger exposure, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:modulus-of-total-boundedness-carrier}. Its visible rows are precisely $X,D,S,T,K,L,H,C,P,N$.

The tolerance schedule is read through $D$ and $S$ before any finite-net row is consumed. The total-bounded row $T$ supplies the finite-net source, while $K$ and $L$ display the center bundle and coverage ledger for that tolerance.

The structural rows $H,C,P,N$ transport, replay, source, and name the same finite surface. Since the carrier has no open-cover, selected-set, quotient-completion, choice, or ambient-completeness coordinate, the NameCert obligations are exactly the displayed schedule rows.
\end{proof}

\begin{theorem}[Modulus of total boundedness compact handoff]
\label{thm:modulus-of-total-boundedness-compact-handoff}
Every $\CompactMetricUp$ or continuous-route consumer of an accepted $\ModulusOfTotalBoundednessUp$ packet must read the dyadic tolerance row $D$, the StreamName schedule row $S$, the $\TotallyBoundedUp$ source row $T$, the center bundle $K$, and the coverage ledger $L$ before it consumes compact finite-net data. The handoff exports a schedule-indexed finite net and no open-cover compactness, selected subcover, countable choice, selected representative, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the NameCert obligation theorem. It places the tolerance request, finite observation schedule, total-bounded source, center bundle, and coverage ledger among the visible rows of every accepted packet.

A compact-metric or continuous-route read needs the finite-net data. That data occurs only in $T,K,L$, and those rows are downstream of the dyadic tolerance and schedule rows $D,S$ in the carrier.

Thus the consumer receives a finite dyadic epsilon-net schedule, not an open-cover compactness principle. The excluded coordinates do not occur in the carrier, so they cannot be exported by the handoff.
\end{proof}

\closureat{ModulusOfTotalBoundednessUp}{seedStr}

\begin{closurestatus}{\ModulusOfTotalBoundednessUp}
  \constructivestory{A $\ModulusOfTotalBoundednessUp$ packet is generated from a MetricSpace row, a DyadicRatCore positive tolerance request, a StreamName finite schedule, a TotallyBounded finite-net source, a ProbeBundle center row, a coverage ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:modulus-of-total-boundedness-carrier}, \autoref{thm:modulus-of-total-boundedness-namecert-obligations}, and \autoref{thm:modulus-of-total-boundedness-compact-handoff} seed the explicit dyadic epsilon-net schedule route for total-bounded and compact-metric consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected subcovers, selected representatives, quotient completion, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic tolerance exposure, finite schedule exposure, total-bounded source exposure, finite center-bundle exposure, coverage-ledger exposure, compact handoff, nonescape, transport, replay, provenance, and local naming for BEDC.Derived.ModulusOfTotalBoundednessUp.}
\end{closurestatus}
