\chapter{A Concrete Naming Certificate for $\RegularCauchyHausdorffReflectionUp$}
\label{ch:concrete-instances-regular-cauchy-hausdorff-reflection-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyHausdorffReflectionUp$ packet records the separated-completion reflection route for regular Cauchy rational names as finite BEDC NameCert data. It sits over the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the uniqueness boundary of \autoref{ch:concrete-instances-regular-cauchy-uniqueness-namecert}. The packet lets a Real-facing consumer treat two representative regular Cauchy names as the same separated reflection point only after the displayed finite windows, dyadic budgets, and uniqueness ledger have been exposed.

\begin{definition}[Regular-Cauchy Hausdorff-reflection carrier]
\label{def:regular-cauchy-hausdorff-reflection-carrier}
A $\RegularCauchyHausdorffReflectionUp$ carrier is a finite $\BHist$ packet
$$
R=(X,Y,S,T,D,U,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the first $\RegSeqRatUp$ regular rational Cauchy name row.
\item $Y$ is the second $\RegSeqRatUp$ regular rational Cauchy name row presented to the same separated-reflection request.
\item $S$ and $T$ are the paired $\StreamNameUp$ finite-window rows through which $X$ and $Y$ are observed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to those windows.
\item $U$ is the $\RegularCauchyUniquenessUp$ row witnessing that the displayed tail comparisons force separated agreement.
\item $E$ is the terminal $\RealUp$ seal row available only after $X,Y,S,T,D,U$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two regular names, stream windows, dyadic ledger, uniqueness row, Real seal, and local certificate rows.
\item $C$ records the displayed $\Cont$ replay from a reflection request to the paired windows, dyadic tolerance ledger, uniqueness row, and terminal Real seal.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyHausdorffReflectionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchyUniquenessUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyHausdorffReflectionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,S,T,D,U,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected representatives, host real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Regular-Cauchy Hausdorff-reflection NameCert obligations]
\label{thm:regular-cauchy-hausdorff-reflection-namecert-obligations}
For every accepted $\RegularCauchyHausdorffReflectionUp$ carrier $R=(X,Y,S,T,D,U,E,H,C,P,N)$, the local $\NameCert_{\RegularCauchyHausdorffReflectionUp}$ surface consists exactly of carrier admission for two $\RegSeqRatUp$ source rows, paired $\StreamNameUp$ finite windows, the $\DyadicRatCoreUp$ tolerance ledger, the $\RegularCauchyUniquenessUp$ separated-agreement row, the terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No NameCert obligation may replace these rows by quotient stream equality, selected representatives, host real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyHausdorffReflectionUp.RegularCauchyHausdorffReflectionTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-hausdorff-reflection-carrier}. The only displayed coordinates are $X,Y,S,T,D,U,E,H,C,P,N$.

The two regular rational names are compared through the paired stream windows $S,T$ and the dyadic tolerance ledger $D$. The separated-agreement row $U$ is therefore a displayed uniqueness boundary, not a quotient of streams or a host equality proof.

The terminal Real seal $E$ is downstream of that boundary. Transport, replay, provenance, and local naming are supplied by $H,C,P,N$, and no excluded quotient, selector, host-equality, choice, trichotomy, or ambient-completeness coordinate can be projected from the carrier.
\end{proof}

\begin{theorem}[Regular-Cauchy Hausdorff-reflection representative independence]
\label{thm:regular-cauchy-hausdorff-reflection-representative-independence}
Every $\RealUp$ seal read accepted by a $\RegularCauchyHausdorffReflectionUp$ packet is independent of the chosen representative regular Cauchy name in the following BEDC sense: if the two presented $\RegSeqRatUp$ rows are compared through the displayed $\StreamNameUp$ windows and $\DyadicRatCoreUp$ tolerance ledger, then the terminal seal can distinguish them only through the $\RegularCauchyUniquenessUp$ row. The packet exports no quotient stream equality, selected representative, host real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyHausdorffReflectionUp.RegularCauchyHausdorffReflectionRepresentativeIndependence}
\begin{proof}
Begin with an accepted carrier $R=(X,Y,S,T,D,U,E,H,C,P,N)$. The rows $X$ and $Y$ are not presented as completed real objects; they are presented as regular rational names observed through finite stream windows.

The dyadic ledger $D$ binds the comparison budget for those windows, and the uniqueness row $U$ is the only row that can turn the displayed tail comparison into separated agreement. Thus any Real-facing read of $E$ must pass through the same finite comparison route.

The rows $H,C,P,N$ transport, replay, source, and name this route without adding analytic content. Since the carrier contains no further equality coordinate, changing representatives cannot be detected except through the displayed uniqueness row.
\end{proof}

\begin{theorem}[Regular-Cauchy Hausdorff-reflection Real seal non-escape]
\label{thm:regular-cauchy-hausdorff-reflection-real-seal-nonescape}
No terminal $\RealUp$ seal consumer accepted by a $\RegularCauchyHausdorffReflectionUp$ packet can bypass the displayed route
$$
\RegSeqRatUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegularCauchyUniquenessUp,\ \RealUp .
$$
In particular, the separated reflection supplies representative independence for the Real seal without quotient streams, host real equality, selected representatives, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyHausdorffReflectionUp.RegularCauchyHausdorffReflectionCarrier\_real\_seal\_nonescape}
\begin{proof}
Read the carrier coordinates in order. The terminal row $E$ appears only after the two regular rational names, paired stream windows, dyadic tolerance ledger, and uniqueness row have been displayed.

Apply \autoref{thm:regular-cauchy-hausdorff-reflection-namecert-obligations}. The local NameCert surface exposes exactly those rows, with $H,C,P,N$ preserving the same route for downstream consumers.

The advertised route is therefore the only public path to the Real seal. Since no excluded equality or choice coordinate occurs in the carrier, the seal cannot escape through quotient streams, host equality, representatives selected outside the packet, countable choice, trichotomy, or ambient completeness.
\end{proof}

\falsifiablePrediction{An accepted $\RegularCauchyHausdorffReflectionUp$ consumer that reaches the terminal RealUp seal without reading two RegSeqRat source rows, paired StreamName windows, a DyadicRatCore tolerance ledger, and a RegularCauchyUniqueness row refutes the carrier surface.}

\independenceWitness{regseqrat, streamname, dyadicratcore, real, regularcauchyuniqueness: $\RegularCauchyHausdorffReflectionUp$ is not bijective to any listed sibling because it binds two regular rational representatives to one separated uniqueness row and one downstream Real seal.}

\closureat{RegularCauchyHausdorffReflectionUp}{seedStr}

\begin{closurestatus}{\RegularCauchyHausdorffReflectionUp}
  \constructivestory{A $\RegularCauchyHausdorffReflectionUp$ packet is generated from two RegSeqRat source rows, paired StreamName finite windows, a DyadicRatCore tolerance ledger, a RegularCauchyUniqueness separated-agreement row, a terminal RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-hausdorff-reflection-carrier}, \autoref{thm:regular-cauchy-hausdorff-reflection-namecert-obligations}, \autoref{thm:regular-cauchy-hausdorff-reflection-representative-independence}, and \autoref{thm:regular-cauchy-hausdorff-reflection-real-seal-nonescape} seed the separated reflection route for regular Cauchy representatives and Real seal consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected representatives, host real equality, countable choice, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{A formal route can encode the displayed carrier and prove the finite NameCert obligation surface, representative-independence handoff, and Real seal non-escape theorem.}
\end{closurestatus}
