\chapter{A Concrete Naming Certificate for $\BishopLocatedLimitUp$}
\label{ch:concrete-instances-bishop-located-limit-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopLocatedLimitUp$ packet records the located-limit surface of a displayed constructive real sequence as finite NameCert data. It sits after the finite window schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the located-limit interface of \autoref{ch:concrete-instances-locatedlimit-namecert}, the located-real enclosure route of \autoref{ch:concrete-instances-locatedreal-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives the L10 Real and Completion route a traditional constructive limit certificate without quotient stream equality, selected host limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop located-limit carrier]
\label{def:bishop-located-limit-carrier}
A $\BishopLocatedLimitUp$ carrier is a finite $\BHist$ packet
$$
B=(S,D,R,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ schedule naming the finite windows inspected for the limit request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to those windows.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same schedule and tolerance data.
\item $L$ is the located-limit witness row, recording the displayed modulus and enclosure data for the requested tail.
\item $E$ is the terminal $\RealUp$ seal row, available only after $S,D,R,L$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the schedule, tolerance, readback, located-limit, and Real-seal rows.
\item $C$ records displayed $\Cont$ replay from a precision request through the schedule, tolerance ledger, readback, located-limit witness, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\BishopLocatedLimitUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\LocatedLimitUp$, $\LocatedRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopLocatedLimitUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,D,R,L,E,H,C,P,N$. It has no coordinate for quotient stream equality, a selected limit, quotient real equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop located-limit NameCert obligations]
\label{thm:bishop-located-limit-namecert-obligations}
For every accepted $\BishopLocatedLimitUp$ carrier $B=(S,D,R,L,E,H,C,P,N)$, the local $\NameCert_{\BishopLocatedLimitUp}$ surface consists exactly of StreamName schedule exposure, DyadicRatCore tolerance accounting, RegSeqRat readback, located-limit witness display, Real-seal ordering, componentwise transport, continuation replay, package provenance, and local naming. Every Real or Completion consumer must read the finite route
$$
S,D \longmapsto R \longmapsto L \longmapsto E
$$
together with $H,C,P,N$ before treating the packet as a Bishop located limit.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-located-limit-carrier}. The tuple exposes exactly the schedule, tolerance, readback, located-limit, Real-seal, transport, replay, provenance, and local naming rows.

The constructive source is finite. The rows $S$ and $D$ name the inspected windows and tolerances, and $R$ reads those same windows as regular rational data rather than as host sequence equality.

The limit side is then read through $L$ and $E$. The row $L$ supplies the located witness for the displayed request, and the row $E$ is downstream from that witness, so a Real-facing consumer cannot bypass the located route.

Transport through $H$ and replay through $C$ preserve the same ordering, while $P$ and $N$ record provenance and local naming. Since the carrier contains no quotient stream equality, selected limit, countable-choice schedule, trichotomy decision, or ambient-completeness row, the listed projections exhaust the NameCert obligations.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopLocatedLimitUp$ read used by a Real or Completion consumer displays one $\StreamNameUp$ schedule, one $\DyadicRatCoreUp$ tolerance ledger, one $\RegSeqRatUp$ readback row, one located-limit witness, one terminal $\RealUp$ seal row, and the structural rows $H,C,P,N$.}

\independenceWitness{streamname, dyadicratcore, regseqrat, locatedlimit, locatedreal, real: $\BishopLocatedLimitUp$ is not bijective to any listed sibling because it binds the Bishop located-limit witness to the same finite schedule, dyadic tolerance ledger, regular rational readback, and terminal Real seal.}

\closureat{BishopLocatedLimitUp}{seedStr}

\begin{closurestatus}{\BishopLocatedLimitUp}
  \constructivestory{A $\BishopLocatedLimitUp$ packet is generated from a StreamName finite schedule, a DyadicRatCore tolerance ledger, a RegSeqRat readback row, a located-limit witness, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-located-limit-carrier} and \autoref{thm:bishop-located-limit-namecert-obligations} seed the finite Bishop located-limit route over StreamName, DyadicRatCore, RegSeqRat, LocatedLimit, LocatedReal, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Real completeness, quotient stream equality, selected host limits, quotient real equality, countable choice, trichotomy, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, schedule exposure, tolerance accounting, regular readback ordering, located-limit witness display, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopLocatedLimitUp.}
\end{closurestatus}
