\chapter{A Concrete Naming Certificate for $\MetaCICResidualSubstitutionCompatibilityUp$}
\label{ch:concrete-instances-metacic-residual-substitution-compatibility-namecert}
\origin{human}

Following Tait--Martin-Lof and Barendregt on residuals, parallel reduction, and confluence discipline, the $\MetaCICResidualSubstitutionCompatibilityUp$ packet records the finite boundary where a beta-parallel branch and a substitution replay must meet before the MetaCIC confluence route may use the conditional diamond bridge. It sits over the audit map of \autoref{ch:metacic-confluence-audit-map} and names the residual-substitution input as packet data rather than as a global Church--Rosser theorem. The packet does not claim full closed Church--Rosser, arbitrary closed-source confluence, or an unrestricted substitution theorem.

\begin{definition}[MetaCIC residual-substitution compatibility carrier]
\label{def:metacic-residual-substitution-compatibility-carrier}
A $\MetaCICResidualSubstitutionCompatibilityUp$ carrier is a finite $\BHist$ packet
$$
M=(s,t,b,j,g,a,h,c,p,n)
$$
with the following displayed rows:
\begin{enumerate}
\item $s$ is the source term row whose beta-parallel residual branch is inspected.
\item $t$ is the substituted term row, storing the finite substitution request and the target occurrence window.
\item $b$ is the parallel branch row, displaying the left and right beta-parallel steps before any join is named.
\item $j$ is the residual join row, recording the candidate common reduct obtained after substitution replay and residual transport.
\item $g$ is the closedness guard row, saying exactly which source and substitution windows are closed enough for the guarded handoff.
\item $a$ is the atom-shape separation row, keeping atom, application, lambda, Pi, and beta-redex cases visibly disjoint.
\item $h$ records componentwise $\hsame$ transport for source, substitution, branch, residual join, closedness guard, atom-shape separation, replay, provenance, and local naming rows.
\item $c$ records displayed $\Cont$ replay from the source term through substitution, parallel branching, residual join construction, closedness guarding, and atom-shape separation.
\item $p$ is the $\Pkg$ provenance over $\MetaCICResidualSubstitutionCompatibilityUp$, MetaCIC beta-parallel reduction, residual joins, closedness guards, atom-shape separation, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $n$ is the local $\NameCert_{\MetaCICResidualSubstitutionCompatibilityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $s,t,b,j,g,a,h,c,p,n$. It has no coordinate for a completed parallel diamond, full closed Church--Rosser, arbitrary closed-source confluence, or an unguarded substitution principle.
\end{definition}

\begin{theorem}[MetaCIC residual-substitution compatibility NameCert obligations]
\label{thm:metacic-residual-substitution-compatibility-namecert-obligations}
For every accepted $\MetaCICResidualSubstitutionCompatibilityUp$ carrier
$$
M=(s,t,b,j,g,a,h,c,p,n),
$$
the local $\NameCert_{\MetaCICResidualSubstitutionCompatibilityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source term, substituted term, parallel branch, residual join, closedness guard, atom-shape separation, transport, replay, provenance, and local naming rows;
\item branch-shape disjointness, requiring atom, application, lambda, Pi, and beta-redex branches to be separated by $a$ before a residual join row is accepted;
\item substitution residual replay, requiring $c$ to display how the substituted term row and beta-parallel branch row reach the same candidate join $j$;
\item closed-source guard, requiring $g$ to expose the exact closedness assumptions consumed by the guarded compatibility packet;
\item non-claim of full closed Church--Rosser, requiring the packet to remain an input boundary for the conditional confluence bridge rather than a proof of arbitrary closed-source confluence.
\end{enumerate}
No obligation is stored outside $s,t,b,j,g,a,h,c,p,n$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-residual-substitution-compatibility-carrier}. The source term, substituted term, branch, residual join, closedness guard, and atom-shape separation rows are the only computational coordinates.

The branch-shape row $a$ fixes the case split before the join row is read. Thus a beta-redex residual branch cannot be silently identified with an atom, application, lambda, or Pi shape.

Replay then supplies the compatibility boundary. The row $c$ records the finite route from substitution and beta-parallel branching to the candidate join $j$, while $g$ states the closedness guard consumed by that route.

Finally $h,p,n$ transport, source, and name exactly the displayed packet. Since full closed Church--Rosser and arbitrary closed-source confluence are not carrier coordinates, they are not exported by this NameCert surface.
\end{proof}

\falsifiablePrediction{Every accepted $\MetaCICResidualSubstitutionCompatibilityUp$ read displays source term, substituted term, parallel branch, residual join, closedness guard, atom-shape separation, hsame transport, Cont replay, Pkg provenance, and local naming rows before the conditional MetaCIC confluence bridge can consume it.}

\independenceWitness{metacic-confluence-audit: $\MetaCICResidualSubstitutionCompatibilityUp$ is not a completed confluence theorem because it carries only the finite residual-substitution compatibility boundary consumed by the conditional parallel-diamond route.}

\closureat{MetaCICResidualSubstitutionCompatibilityUp}{seedStr}

\begin{closurestatus}{\MetaCICResidualSubstitutionCompatibilityUp}
  \constructivestory{A $\MetaCICResidualSubstitutionCompatibilityUp$ packet is generated from source term, substituted term, parallel branch, residual join, closedness guard, atom-shape separation, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-residual-substitution-compatibility-carrier} and \autoref{thm:metacic-residual-substitution-compatibility-namecert-obligations} seed the finite residual-substitution compatibility boundary consumed by the conditional MetaCIC confluence bridge.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim full closed Church--Rosser, arbitrary closed-source confluence, unguarded substitution compatibility, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, branch-shape disjointness, substitution residual replay, closed-source guard, and conditional confluence handoff alignment for BEDC.MetaCIC.BetaParallelSubstitutionCompatibility.}
\end{closurestatus}
