\chapter{A Concrete Naming Certificate for $\KolmogorovContinuityUp$}
\label{ch:concrete-instances-kolmogorov-continuity-namecert}
\origin{human}

Following Kolmogorov's continuity criterion, the $\KolmogorovContinuityUp$ packet records a finite-modulus continuity test for stochastic-process windows as displayed BEDC data. It consumes the probability carrier of \autoref{ch:concrete-instances-probspace-namecert}, the random-variable preimage surface of \autoref{ch:concrete-instances-randomvar-namecert}, the metric-space rows of \autoref{ch:concrete-instances-metric-space-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only the finite difference and modulus ledger; it is not a host path-continuity theorem, a choice of continuous modification, a quotient sample-path object, or an ambient $\RealUp$ completeness principle.

\begin{definition}[Kolmogorov continuity carrier]
\label{def:kolmogorov-continuity-carrier}
A $\KolmogorovContinuityUp$ carrier is a finite $\BHist$ packet
$$
K=(I,M,S,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite difference ledger, listing inspected process windows, endpoint pairs, random-variable rows, metric-distance requests, and the probability-space row used for each two-time difference.
\item $M$ is the moment and finite-modulus ledger. It records the displayed exponent, scale, tolerance, and decay rows that certify the Kolmogorov bound on the inspected two-time differences.
\item $S$ is the $\StreamNameUp$ window row that names the finite time and sample observations read by the process consumer.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational moment and modulus bounds extracted from $I,M,S$.
\item $R$ is the $\RealUp$ seal row for the real-valued bound reached only after the displayed regular rational readback.
\item $E$ is the $\MetricSpaceUp$ and $\RandomVarUp$ endpoint-exposure row, keeping metric distance and random-variable measurability attached to the same inspected two-time difference.
\item $H$ records componentwise $\hsame$ transport for two-time difference rows, moment/modulus rows, StreamName windows, RegSeqRat readback, Real seals, metric/random-variable exposure, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the finite route
$$
I,M,S \longmapsto Q \longmapsto R \longmapsto E \longmapsto H .
$$
\item $P$ is the $\Pkg$ provenance over $\KolmogorovContinuityUp$, $\ProbSpaceUp$, $\RandomVarUp$, $\MetricSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\KolmogorovContinuityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,M,S,Q,R,E,H,C,P,N$. It has no coordinate for ambient path continuity, a selected continuous modification, quotient sample paths, countable-choice schedules, host equality of stochastic processes, or $\RealUp$ completeness.
\end{definition}

\begin{theorem}[KolmogorovContinuityUp NameCert obligations]
\label{thm:kolmogorov-continuity-namecert-obligations}
For every accepted $\KolmogorovContinuityUp$ carrier
$$
K=(I,M,S,Q,R,E,H,C,P,N),
$$
the local $\NameCert_{\KolmogorovContinuityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item two-time difference admission for $I$, requiring every inspected endpoint pair, process row, random-variable row, metric-distance request, and probability-space row to be displayed;
\item moment and modulus admission for $M$, requiring the exponent, scale, tolerance, and decay rows used by the criterion to be named as finite ledger data;
\item StreamName observation for $S$, requiring all time and sample windows consumed by the two-time difference rows to be displayed before any regular-rational readback;
\item regular-rational readback for $Q$, requiring moment and modulus bounds to pass through the accepted $\RegSeqRatUp$ surface;
\item Real seal exposure for $R$, requiring every real-valued bound to be reached only after $Q$;
\item metric and random-variable endpoint exposure for $E$, requiring distance and measurability rows to remain attached to the same inspected two-time difference;
\item transport, replay, provenance, and local naming through $H,C,P,N$, preserving exactly the displayed continuity-criterion packet.
\end{enumerate}
No Kolmogorov continuity obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:kolmogorov-continuity-carrier}. The two-time difference ledger $I$ supplies the only endpoint pairs and stochastic-process rows available to a consumer, and each such row already displays its $\ProbSpaceUp$, $\RandomVarUp$, and $\MetricSpaceUp$ support.

Read the moment and finite-modulus ledger $M$ together with the observation row $S$. These rows name the inspected windows, exponents, scales, tolerances, and decay data before any readback can be exported.

The regular-rational row $Q$ is the only route from the finite moment/modulus ledger to a numerical bound, and the real seal $R$ is downstream of $Q$. The endpoint-exposure row $E$ keeps the metric and random-variable coordinates attached to the same two-time difference rather than letting them become ambient path data.

Finally $H,C,P,N$ transport, replay, source, and name the same tuple. Since the carrier has no coordinate for ambient path continuity, selected modifications, quotient sample paths, countable choice, host process equality, or $\RealUp$ completeness, the listed rows exhaust the local naming surface.
\end{proof}

\begin{theorem}[KolmogorovContinuityUp finite-modulus route]
\label{thm:kolmogorov-continuity-finite-modulus-route}
Every continuity-facing consumer of an accepted $\KolmogorovContinuityUp$ packet reads the criterion through the finite route
$$
\ProbSpaceUp,\ \RandomVarUp,\ \MetricSpaceUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
Concretely, a two-time difference row first displays its probability-space, random-variable, and metric-distance support; the same request then exposes a finite StreamName window, a moment/modulus ledger, a regular rational readback, and only then a terminal real seal. The route exports a finite-modulus continuity criterion, not ambient path continuity, a chosen continuous modification, quotient sample paths, host process equality, countable choice, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(I,M,S,Q,R,E,H,C,P,N)$. By \autoref{thm:kolmogorov-continuity-namecert-obligations}, a two-time difference read must first display the rows in $I$ and the endpoint support in $E$, so the probability, random-variable, and metric data are fixed before a continuity-facing consumer sees a bound.

The same obligation surface places the finite StreamName window $S$ and moment/modulus ledger $M$ before the regular-rational readback $Q$. Thus the criterion is read from displayed windows and finite decay rows rather than from an infinite sample path.

The real-facing step is controlled by $R$, which is downstream of $Q$. Componentwise $\hsame$ transport and $\Cont$ replay preserve this order, while $\Pkg$ provenance and the local $\NameCert$ row name exactly the same route.

Therefore every consumer factors through the displayed finite-modulus path. The excluded path-continuity, modification-choice, quotient-sample-path, host-equality, countable-choice, and completeness claims are absent from the carrier and cannot be recovered from the packet.
\end{proof}

\closureat{KolmogorovContinuityUp}{seedStr}

\begin{closurestatus}{\KolmogorovContinuityUp}
  \constructivestory{A $\KolmogorovContinuityUp$ packet is generated from finite two-time difference rows, moment and modulus ledger rows, StreamName windows, RegSeqRat readback, Real seals, metric and random-variable endpoint exposure, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kolmogorov-continuity-carrier}, \autoref{thm:kolmogorov-continuity-namecert-obligations}, and \autoref{thm:kolmogorov-continuity-finite-modulus-route} seed the finite-modulus continuity criterion over probability, random-variable, metric, StreamName, RegSeqRat, Real, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient path continuity, chosen continuous modifications, quotient sample paths, countable choice, host process equality, RealUp completeness, Lean verification, or a standard bridge.}
  \upgradepath{Obligation closure requires checked two-time difference admission, moment/modulus admission, StreamName observation, RegSeqRat readback, Real seal exposure, endpoint exposure, and transport/provenance/name exhaustion for BEDC.Derived.KolmogorovContinuityUp.}
\end{closurestatus}
