\chapter{A Concrete Naming Certificate for $\TaggedRealPartitionUp$}
\label{ch:concrete-instances-tagged-real-partition-namecert}
\origin{human}

Following Bishop and Bridges constructive integration, the $\TaggedRealPartitionUp$ packet records a finite partition of a located real interval together with a displayed tag inside each cell. It refines the located partition carrier of \autoref{ch:concrete-instances-located-real-interval-partition-namecert} and the oscillation-controlled partition carrier of \autoref{ch:concrete-instances-finite-oscillation-partition-namecert}; it also reads its endpoint and tag data through the $\StreamNameUp$ source of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies the finite tag-bearing surface needed by L10 integration and oscillation routes without replacing it by an untagged mesh, a host partition object, selected representatives, quotient real equality, countable choice, or ambient completeness.

\begin{definition}[Tagged real partition carrier]
\label{def:tagged-real-partition-carrier}
A $\TaggedRealPartitionUp$ carrier is a finite $\BHist$ packet
$$
T=(I,M,A,G,O,S,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the source $\LocatedRealIntervalPartitionUp$ row exposing the located interval, finite cell order, endpoint containment, and mesh precision.
\item $M$ is the finite mesh row inherited from $I$, listing adjacent cells and the common refinement ledger used by later integration consumers.
\item $A$ is the cell-containment row, certifying for every mesh cell that its endpoints and rational witness rows remain inside the located interval source.
\item $G$ is the tag row family, assigning to every displayed cell a tag history whose $\StreamNameUp$ and $\RegSeqRatUp$ reads certify containment in that same cell before any $\RealUp$ seal is consumed.
\item $O$ is the oscillation and modulus ledger, recording the tolerance request, the cellwise oscillation bound, and the refinement compatibility supplied by $\FiniteOscillationPartitionUp$.
\item $S$ is the finite $\StreamNameUp$ window family opened for interval endpoints, cell endpoints, and tags.
\item $R$ is the $\RegSeqRatUp$ readback family for the same finite windows and mesh precision.
\item $E$ is the terminal $\RealUp$ seal family reached only after the source interval, cell containment, tag containment, oscillation ledger, window, and regular readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for $I,M,A,G,O,S,R,E$ and for the replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tagged-partition read through
$$
I,M,A,G,O,S,R,E \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\TaggedRealPartitionUp$, $\LocatedRealIntervalPartitionUp$, $\FiniteOscillationPartitionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\TaggedRealPartitionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only by these displayed interval-source, mesh, containment, tag, oscillation, window, readback, seal, transport, replay, provenance, and local naming rows. It has no coordinate for a host tagged partition, an unbounded tag selector, quotient real equality, chosen completed tag values, countable choice, or ambient real completeness.
\end{definition}

\begin{theorem}[Tagged real partition NameCert obligations]
\label{thm:tagged-real-partition-namecert-obligations}
For every accepted $\TaggedRealPartitionUp$ carrier $T=(I,M,A,G,O,S,R,E,H,C,P,N)$, the local $\NameCert_{\TaggedRealPartitionUp}$ surface consists exactly of carrier admission, located interval and mesh exposure through $I,M$, cell-containment certification through $A$, tag containment through $G$, oscillation and modulus accounting through $O$, finite $\StreamNameUp$ windows through $S$, $\RegSeqRatUp$ readback through $R$, terminal $\RealUp$ seals through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.

Every integration-facing or oscillation-facing read of the tagged partition must therefore pass through the displayed finite mesh, tag-containment, oscillation, window, readback, and seal rows before any terminal real-value consumer is allowed to inspect the packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:tagged-real-partition-carrier}. The tuple lists the only rows available to a tagged-partition consumer: the interval source, mesh, containment ledger, tag rows, oscillation ledger, finite windows, regular readbacks, real seals, transport, replay, provenance, and local naming rows.

The source interval and cell obligations are $I,M,A$. The located partition row supplies the interval and mesh; the containment row attaches each cell to the same source, so a tag cannot be read against a detached host interval.

The tag and oscillation obligations are $G,O$. The tag row certifies cell membership for each tag through the same finite-window and regular-readback route, while the oscillation row records the tolerance and refinement ledger inherited from the oscillation-partition packet.

The readback and seal obligations are $S,R,E$. A consumer reaches the StreamName windows only after the interval, cell, tag, and oscillation rows are visible, then reads the regular rational rows and finally the terminal Real seal.

The structural rows $H,C,P,N$ transport, replay, package, and name exactly this route. Since the carrier has no coordinate for a host tagged partition, an unbounded selector, quotient real equality, chosen completed tag values, countable choice, or ambient completeness, the displayed NameCert obligations exhaust the accepted packet.
\end{proof}

\closureat{TaggedRealPartitionUp}{seedStr}

\begin{closurestatus}{\TaggedRealPartitionUp}
  \constructivestory{A $\TaggedRealPartitionUp$ packet is generated from a LocatedRealIntervalPartitionUp source, finite mesh and cell-containment rows, per-cell tag rows, oscillation and modulus ledgers, StreamName windows, RegSeqRat readback, RealUp seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:tagged-real-partition-carrier} and \autoref{thm:tagged-real-partition-namecert-obligations} seed the finite tag-bearing partition interface for L10 integration and oscillation consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close integration convergence, Darboux sums, quotient real equality, selected tag values, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, cell containment, tag containment, oscillation-modulus accounting, StreamName windows, RegSeqRat readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.TaggedRealPartitionUp.}
\end{closurestatus}
