\chapter{A Concrete Naming Certificate for $\CauchyApproximationTreeUp$}
\label{ch:concrete-instances-cauchy-approximation-tree-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CauchyApproximationTreeUp$ packet records a finite branching approximation surface over the L10 Cauchy spine: each active branch carries a displayed tolerance window, a dyadic approximation row, a regular-rational readback row, and a terminal Real seal. It sits between the dyadic endpoint ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the Cauchy route of \autoref{ch:concrete-instances-cauchy-namecert}. The packet gives Real and Completion consumers a finite approximation tree without quotient streams, selected limits, countable choice, host real equality, trichotomy, or ambient completeness.

\begin{definition}[Cauchy approximation tree carrier]\label{def:cauchy-approximation-tree-carrier}
A $\CauchyApproximationTreeUp$ carrier is a finite $\BHist$ packet
$$
T=(V,E,B,D,S,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $V$ is the finite tree-node row, listing the nodes presently opened by the approximation packet.
\item $E$ is the finite edge and parenthood row, recording the branch relation among the nodes in $V$.
\item $B$ is the branch-window row, assigning each active branch the finite tolerance window currently inspected.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic approximants, radius comparisons, and the error rows attached to each branch window.
\item $S$ is the $\StreamNameUp$ observation schedule opened by the branch windows and no hidden stream coordinates.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed stream windows and dyadic tolerance rows.
\item $L$ is the $\RealUp$ seal row reached only after the node, branch-window, dyadic, stream, and regular-readback rows have been exposed.
\item $H$ records componentwise $\hsame$ transport for tree nodes, branch windows, dyadic rows, stream schedules, regular readbacks, Real seals, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite tree branch through $B,D,S,R$ and into the terminal Real seal $L$.
\item $P$ is the $\Pkg$ provenance over $\CauchyApproximationTreeUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyApproximationTreeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $V,E,B,D,S,R,L,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy approximation tree NameCert obligations]\label{thm:cauchy-approximation-tree-namecert-obligations}
For every accepted $\CauchyApproximationTreeUp$ carrier $T=(V,E,B,D,S,R,L,H,C,P,N)$, the local $\NameCert_{\CauchyApproximationTreeUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the tree-node row, edge row, branch windows, dyadic tolerance ledger, stream schedule, regular readback, Real seal, transport, replay, provenance, and local naming rows;
\item tree finiteness, requiring every inspected branch to be generated by the finite node and edge rows $V,E$;
\item branch-window exactness, requiring each active branch to read its tolerance window from $B$ before any dyadic approximation in $D$ is accepted;
\item dyadic and stream exactness, requiring $D$ and $S$ to expose only the dyadic approximants and finite observations demanded by the displayed branch windows;
\item regular readback and Real-seal boundary, requiring $R$ and $L$ to remain downstream of $V,E,B,D,S$ and never to serve as selected limits or host equality objects;
\item componentwise transport and replay, requiring $H$ and $C$ to preserve exactly the displayed finite branch route;
\item provenance and local naming, requiring $P$ and $N$ to export the route over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\CauchyUp$ without adding quotient equality, choice, trichotomy, or ambient completeness.
\end{enumerate}
No approximation-tree obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-approximation-tree-carrier}. The accepted packet displays exactly the finite node row $V$, edge row $E$, branch windows $B$, dyadic ledger $D$, stream schedule $S$, regular readback $R$, Real seal $L$, and structural rows $H,C,P,N$.

Tree finiteness and branch-window exactness follow from the row order. A consumer first reads a node and its branch relation from $V,E$; only then may it inspect the branch tolerance window $B$ and the dyadic approximation row $D$ attached to that branch.

The stream and readback rows are downstream of the same branch window. The schedule $S$ opens only the finite observations demanded by $B$, and $R$ records the regular-rational data justified by $D$ and $S$.

Finally, the Real seal row $L$ is terminal for this finite branch route. The transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$ preserve and name the same displayed packet, so no quotient stream equality, selected limit, countable-choice selector, host real equality, trichotomy principle, or ambient completeness theorem can become a local obligation.
\end{proof}

\begin{theorem}[Cauchy approximation tree branch readback]\label{thm:cauchy-approximation-tree-branch-readback}
Every $\RealUp$ or $\CauchyUp$ consumer of an accepted $\CauchyApproximationTreeUp$ carrier reads a branch only through the displayed route
$$
V,E,B,D,S,R,L,H,C,P,N .
$$
Consequently each consumed branch exposes finite tree nodes, branch windows, dyadic tolerance rows, StreamName observations, RegSeqRat readbacks, a Real seal, componentwise transport, displayed replay, provenance, and local naming data. It exposes no quotient stream equality, selected limit, countable choice, host real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Let a Real-facing or Cauchy-facing consumer read an accepted packet $T=(V,E,B,D,S,R,L,H,C,P,N)$. Carrier projection gives access only to the rows named in \autoref{def:cauchy-approximation-tree-carrier}.

The read begins with the finite tree rows $V,E$ and then chooses a displayed branch window in $B$. The dyadic ledger $D$ supplies the approximant and tolerance comparison for that branch, the stream schedule $S$ opens the finite observation windows, and the regular readback row $R$ exposes the rational data that the Real seal may consume.

The terminal row $L$ is therefore reached only after the finite route through $V,E,B,D,S,R$ has been displayed. The structural rows $H,C,P,N$ transport, replay, source, and name the same route without adding any second equality or limit coordinate.

Since the packet has no carrier row for quotient stream equality, selected limits, countable choice, host real equality, trichotomy, or ambient $\RealUp$ completeness, a Real-facing or Cauchy-facing consumer cannot read any of those objects from the local certificate.
\end{proof}

\falsifiablePrediction{Every $\CauchyApproximationTreeUp$ Real-facing or Cauchy-facing read factors through finite tree nodes, branch windows, a DyadicRatCore tolerance ledger, selected StreamName observations, RegSeqRat readbacks, a RealUp seal row, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{dyadicratcore, streamname, regseqrat, real, cauchy: $\CauchyApproximationTreeUp$ is not bijective to any listed sibling because it jointly carries finite tree nodes, branch windows, dyadic tolerance rows, finite stream schedules, regular-rational readback, a terminal Real seal, transport, replay, provenance, and local naming in one branch-indexed packet.}

\closureat{CauchyApproximationTreeUp}{seedStr}

\begin{closurestatus}{\CauchyApproximationTreeUp}
  \constructivestory{A $\CauchyApproximationTreeUp$ packet is generated from finite tree nodes, branch windows, a DyadicRatCore tolerance ledger, StreamName finite observations, RegSeqRat readback rows, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-approximation-tree-carrier}, \autoref{thm:cauchy-approximation-tree-namecert-obligations}, and \autoref{thm:cauchy-approximation-tree-branch-readback} seed the finite branch-indexed route from L10 Cauchy approximation windows to RealUp endpoint consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, host real equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tree finiteness, branch-window exactness, dyadic ledger exactness, stream and readback exactness, Real seal boundary, componentwise transport, replay, provenance, and local naming for BEDC.Derived.CauchyApproximationTreeUp.}
\end{closurestatus}
