\chapter{A Concrete Naming Certificate for $\QuotientFreeCompletionSealUp$}
\label{ch:concrete-instances-quotient-free-completion-seal-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, the $\QuotientFreeCompletionSealUp$ packet records the finite handoff from regular rational Cauchy names to the terminal real seal without quotient streams, selected limits, or ambient completeness. It sits over the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the equivalence-boundary row of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives Real and Completion consumers a single displayed route from named rational approximants to a real-facing seal; it is not a quotient completion, a selected representative, a host limit operation, or a proof of ambient $\RealUp$ completeness.

\begin{definition}[Quotient-free completion seal carrier]
\label{def:quotient-free-completion-seal-carrier}
A $\QuotientFreeCompletionSealUp$ carrier is a finite $\BHist$ packet
$$
Q=(D,S,R,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ tolerance and residue ledger used by every approximation comparison in the packet.
\item $S$ is the $\StreamNameUp$ finite-window row listing the source observations actually inspected before a completion-facing answer is exposed.
\item $R$ is the $\RegSeqRatUp$ regular rational Cauchy readback row attached to the displayed windows and dyadic budgets.
\item $E$ is the $\CauchyEquivalenceSetoidUp$ boundary row. It records only the finite agreement tests available through $D,S,R$, not a quotient object and not host equality of streams.
\item $L$ is the terminal $\RealUp$ seal row reached after the regular rational readback and the equivalence-boundary row have both been displayed.
\item $H$ records componentwise $\hsame$ transport for $D,S,R,E,L$ and for the certificate rows.
\item $C$ records displayed $\Cont$ replay from a completion request through the stream windows, dyadic tolerance ledger, regular rational readback, equivalence boundary, and terminal Real seal.
\item $P$ is the $\Pkg$ provenance over $\QuotientFreeCompletionSealUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\CauchyEquivalenceSetoidUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\QuotientFreeCompletionSealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,S,R,E,L,H,C,P,N$. It has no coordinate for quotient streams, a selected representative regular sequence, a host limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Quotient-free completion seal NameCert obligations]
\label{thm:quotient-free-completion-seal-namecert-obligations}
For every accepted $\QuotientFreeCompletionSealUp$ carrier
$$
Q=(D,S,R,E,L,H,C,P,N),
$$
the local $\NameCert_{\QuotientFreeCompletionSealUp}$ surface consists exactly of carrier admission for the $\DyadicRatCoreUp$ tolerance ledger, $\StreamNameUp$ finite windows, $\RegSeqRatUp$ regular rational readback, $\CauchyEquivalenceSetoidUp$ finite agreement boundary, terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No NameCert obligation may replace these rows by quotient stream equality, a selected limit, a host completion object, or ambient real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:quotient-free-completion-seal-carrier}. The only analytic coordinates are $D,S,R,E,L$, and the only structural coordinates are $H,C,P,N$.

The dyadic row $D$ fixes the comparison budget, while $S$ fixes the finite stream windows available to the completion request. The regular rational row $R$ is therefore read only through displayed observations and displayed tolerances.

The equivalence boundary $E$ is downstream of that route. It records finite agreement tests over $D,S,R$ and does not create a quotient carrier or a host stream-equality predicate.

Finally $L$ is the terminal Real seal reached by replaying $C$ through the same rows, with $H,P,N$ transporting, sourcing, and naming the displayed packet. Since none of the excluded objects occurs as a coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Quotient-free completion seal Real handoff]
\label{thm:quotient-free-completion-seal-real-handoff}
Every $\RealUp$-facing or completion-facing read of an accepted $\QuotientFreeCompletionSealUp$ carrier factors through the finite handoff route
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \CauchyEquivalenceSetoidUp
\longmapsto
\RealUp .
$$
Thus the Real seal is reached only after the displayed dyadic budget, stream-window, regular rational readback, and finite equivalence-boundary rows have been consumed. The route exports no quotient stream, selected representative, selected limit, host completion object, countable choice, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with a Real-facing or completion-facing read of the accepted packet. Carrier admission exposes the terminal row $L$ only as part of the same finite packet as $D,S,R,E$.

Replay the continuation row $C$. The read first consumes the finite windows $S$ and the dyadic ledger $D$, then reads the regular rational row $R$, and only then reaches the equivalence boundary $E$.

The terminal row $L$ is therefore a seal for that displayed route. It does not select a host limit and does not identify a quotient class; it records that the packet has reached the real-facing boundary after the finite readback has been named.

The support rows $H,P,N$ preserve the same route by transport, provenance, and local naming. Since no excluded quotient, selector, or ambient-completeness coordinate is present, no consumer can bypass the displayed handoff.
\end{proof}

\begin{theorem}[Quotient-free completion seal nonescape]
\label{thm:quotient-free-completion-seal-nonescape}
No public consumer accepted by a $\QuotientFreeCompletionSealUp$ packet can extract quotient stream equality, a selected regular Cauchy representative, a selected limit, a host completion object, countable choice, trichotomy, or ambient $\RealUp$ completeness. Every exported completion read remains inside the rows
$$
D,S,R,E,L,H,C,P,N .
$$
\end{theorem}
\begin{proof}
Use \autoref{thm:quotient-free-completion-seal-namecert-obligations}. It identifies the entire local certificate surface with the displayed dyadic, stream-window, regular-readback, equivalence-boundary, Real-seal, transport, replay, provenance, and naming rows.

Apply \autoref{thm:quotient-free-completion-seal-real-handoff}. Any completion-facing read reaches the Real seal only through $D,S,R,E$ and then through the structural rows $H,C,P,N$.

The carrier has no remaining coordinate from which a quotient stream, representative selector, limit selector, host completion object, choice principle, trichotomy branch, or ambient completeness theorem could be projected. Hence every public read is trapped inside the displayed finite route.
\end{proof}

\falsifiablePrediction{An accepted $\QuotientFreeCompletionSealUp$ read is refuted if a consumer reaches a RealUp or completion-facing answer without displaying DyadicRatCore tolerance rows, StreamName finite windows, RegSeqRat regular rational readback, CauchyEquivalenceSetoid finite agreement rows, hsame transport, Cont replay, Pkg provenance, and local NameCert data.}

\independenceWitness{dyadicratcore, streamname, regseqrat, cauchy-equivalence-setoid, real: no listed sibling supplies the whole $\QuotientFreeCompletionSealUp$ packet, because the packet binds dyadic budgets, finite stream windows, regular rational readback, finite agreement boundaries, a terminal Real seal, and local NameCert provenance in one carrier.}

\closureat{QuotientFreeCompletionSealUp}{seedStr}

\begin{closurestatus}{\QuotientFreeCompletionSealUp}
  \constructivestory{A $\QuotientFreeCompletionSealUp$ packet is generated from DyadicRatCore tolerance rows, StreamName finite windows, RegSeqRat regular rational readback, CauchyEquivalenceSetoid finite agreement boundaries, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:quotient-free-completion-seal-carrier}, \autoref{thm:quotient-free-completion-seal-namecert-obligations}, \autoref{thm:quotient-free-completion-seal-real-handoff}, and \autoref{thm:quotient-free-completion-seal-nonescape} seed the quotient-free completion route from finite regular rational readback to a terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected representatives, selected limits, host completion objects, countable choice, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic budget exactness, finite-window readback, regular rational handoff, finite equivalence-boundary exactness, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.QuotientFreeCompletionSealUp.}
\end{closurestatus}
