\chapter{A Concrete Naming Certificate for $\RegularCauchyHeineBorelRouteUp$}
\label{ch:concrete-instances-regular-cauchy-heine-borel-route-namecert}
\origin{human}

Following Heine, Borel, and Bishop--Bridges constructive analysis, the $\RegularCauchyHeineBorelRouteUp$ packet records the explicit finite dyadic closed-interval net route for regular Cauchy real names. It sits over the dyadic arithmetic core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the finite-net Heine--Borel surface of \autoref{ch:concrete-instances-heine-borel-finite-net-namecert}. The chapter is a finite dyadic closed-interval net route over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$; it is not general Heine--Borel for arbitrary subsets of $\RealUp$, does not import open-cover compactness, and does not select limits outside the displayed interval-net data.

\begin{definition}[Regular Cauchy Heine--Borel route carrier]
\label{def:regular-cauchy-heine-borel-route-carrier}
A $\RegularCauchyHeineBorelRouteUp$ carrier is a finite $\BHist$ packet
$$
R=(I,D,S,Q,E,W,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the closed bounded regular-Cauchy interval row, exposing two endpoint $\RegSeqRatUp$ names, their $\StreamNameUp$ finite windows, and the terminal $\RealUp$ endpoint seals.
\item $D$ is the $\DyadicRatCoreUp$ mesh row, recording the finite dyadic subdivision, endpoint comparisons, cell widths, and requested tolerance bound.
\item $S$ is the $\StreamNameUp$ window row that lists the finite observations used to compare each regular-Cauchy endpoint and each inspected interval cell.
\item $Q$ is the $\RegSeqRatUp$ readback row for the endpoint names and the retained dyadic cell names.
\item $E$ is the terminal $\RealUp$ seal row reached only after $D,S,Q$ have been displayed.
\item $W$ is the closed-interval witness row, pairing every retained dyadic cell with its lower and upper endpoint comparisons inside $I$.
\item $F$ is the finite net row, containing only the finite bundle of dyadic cell centers and radius witnesses read by the interval-net route.
\item $H$ records componentwise $\hsame$ transport for the interval, dyadic mesh, stream windows, regular readback, real seal, cell witnesses, finite net, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a closed-interval net request through $I,D,S,Q,E,W,F,H$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyHeineBorelRouteUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\HeineBorelFiniteNetUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyHeineBorelRouteUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,D,S,Q,E,W,F,H,C,P,N$. It has no coordinate for an arbitrary subset of $\RealUp$, arbitrary open covers, selected finite subcovers, quotient real equality, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Regular Cauchy Heine--Borel route obligations]
\label{thm:regular-cauchy-heine-borel-route-obligations}
For every accepted $\RegularCauchyHeineBorelRouteUp$ carrier
$$
R=(I,D,S,Q,E,W,F,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyHeineBorelRouteUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item expose the closed bounded regular-Cauchy interval row $I$ before any interval-net consumer reads a cell;
\item display the dyadic subdivision and tolerance ledger $D$ as the only mesh source;
\item route endpoint and cell observations through the finite $\StreamNameUp$ windows $S$ and the $\RegSeqRatUp$ readback row $Q$;
\item reach the terminal $\RealUp$ seal $E$ only after the dyadic, stream, and regular-rational rows have been displayed;
\item bind each retained dyadic interval cell to the closed interval by the witness row $W$ and export the finite net bundle $F$;
\item preserve the route by componentwise $\hsame$ transport and displayed $\Cont$ replay through $H,C$;
\item source and name the same finite packet through $\Pkg$ provenance $P$ and the local $\NameCert$ row $N$.
\end{enumerate}
No obligation row states general Heine--Borel compactness for arbitrary subsets of $\RealUp$, arbitrary open-cover compactness, a selected subcover functional, quotient real equality, countable choice, selected limits, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:regular-cauchy-heine-borel-route-carrier}. The interval row $I$ is the only source for the closed bounded regular-Cauchy endpoints, and the route cannot inspect an interval cell before those endpoint rows are present.

Next read the dyadic mesh and observation rows. The dyadic ledger $D$ supplies the finite subdivision and the tolerance comparison, while $S$ and $Q$ supply the finite windows and regular-rational readbacks needed to compare endpoint and cell data.

The Real-facing boundary is downstream. The terminal row $E$ is reached only after the dyadic, stream, and regular-rational rows have been displayed, so the route exports a named real seal rather than a host-selected real limit or quotient equality.

Finally the finite-net part is exhausted by $W$ and $F$. The witness row $W$ binds each retained dyadic cell to the closed interval, and $F$ lists the finite cell centers and radii. The structural rows $H,C,P,N$ transport, replay, source, and name this same packet, so no arbitrary subset, open cover, selected subcover, choice, selected-limit, or ambient-completeness coordinate remains.
\end{proof}

\begin{theorem}[Regular Cauchy Heine--Borel finite interval-net route]
\label{thm:regular-cauchy-heine-borel-route-finite-net}
Every $\RealUp$-facing or completion-facing consumer of an accepted $\RegularCauchyHeineBorelRouteUp$ carrier reads the finite route
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp,\ \HeineBorelFiniteNetUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert_{\RegularCauchyHeineBorelRouteUp}.
$$
The route supplies an explicit finite dyadic closed-interval net for closed bounded regular-Cauchy interval data. It supplies no compactness theorem for arbitrary subsets of $\RealUp$, no arbitrary open-cover subcover extraction, no quotient real equality, no countable choice, and no $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Begin with a consumer read of the carrier. The only numerical mesh coordinate is $D$, and every inspected endpoint or cell must be read through the finite windows $S$ and regular-rational row $Q$ before the terminal seal $E$ is available.

The closed-interval part is then bound by $W$. Each retained dyadic cell is paired with displayed lower and upper endpoint comparisons, so the interval-net route remains a finite dyadic route inside the presented closed bounded interval.

The finite net export is exactly $F$. It lists the dyadic centers and radius witnesses read by the Heine--Borel finite-net surface, while $H,C,P,N$ preserve and name the same route. Since the carrier contains none of the excluded arbitrary-subset, open-cover, quotient, choice, selected-limit, or completeness coordinates, every such consumer remains on the displayed finite interval-net route.
\end{proof}

\closureat{RegularCauchyHeineBorelRouteUp}{seedStr}

\begin{closurestatus}{\RegularCauchyHeineBorelRouteUp}
  \constructivestory{A $\RegularCauchyHeineBorelRouteUp$ packet is generated from a closed bounded regular-Cauchy interval row, a DyadicRatCore mesh row, StreamName windows, RegSeqRat readback, a RealUp seal, closed-interval cell witnesses, a finite dyadic net row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-heine-borel-route-carrier}, \autoref{thm:regular-cauchy-heine-borel-route-obligations}, and \autoref{thm:regular-cauchy-heine-borel-route-finite-net} seed the explicit finite dyadic closed-interval net route over DyadicRatCore, StreamName, RegSeqRat, Real, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim general Heine--Borel compactness for arbitrary subsets of $\RealUp$, arbitrary open-cover compactness, selected finite subcovers, quotient real equality, countable choice, selected limits, Lean verification, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic mesh exactness, finite stream-window readback, regular-rational endpoint routing, Real seal nonescape, finite interval-net exposure, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyHeineBorelRouteUp.}
\end{closurestatus}
