\chapter{A Concrete Naming Certificate for $\PartitionBasinPolynomialUp$}
\label{ch:concrete-instances-partition-basin-polynomial-namecert}
\origin{human}

Following finite enumerative combinatorics, the $\PartitionBasinPolynomialUp$ packet records the partition-basin product formula of \autoref{thm:philosophy-partition-basin-polynomial} as displayed NameCert data over block sizes, legal decorations, defect exponents, incidence totals, transport, replay, provenance, and local naming. It sits after the partition carrier of \autoref{ch:concrete-instances-partition-namecert}, the defect-flow partition skeleton of \autoref{ch:concrete-instances-defect-flow-partition-skeleton-namecert}, and the partition-core incidence certificate of \autoref{ch:concrete-instances-partition-core-incidence-certificate-namecert}. The packet names a finite polynomial enumeration surface; it is not a biological stochastic model, a host generating-function oracle, or a quotient-level semantic identification.

\begin{definition}[PartitionBasinPolynomial carrier]
\label{def:partition-basin-polynomial-carrier}
A $\PartitionBasinPolynomialUp$ carrier is a finite $\BHist$ packet
$$
B=(M,S,D,E,F,Q,I,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the finite block-count row for the partition core, and $S$ is the finite block-size ledger $(s_{1},\ldots,s_{m})$.
\item $D$ is the legal-decoration row, recording for each coordinate of block $i$ the admissible subset of the other $m-1$ rows and the private-coordinate exclusion.
\item $E$ is the defect-exponent ledger that assigns exponent weight $q^{r}$ to a coordinate receiving $r$ additional rows.
\item $F$ is the product-formula row
$$
\prod_{i=1}^{m}
\left[
(1+q)^{(m-1)s_{i}}
-
\left((1+q)^{m-1}-1\right)^{s_{i}}
\right].
$$
\item $Q$ is the four-coordinate specialization row for the five partition types $4$, $3+1$, $2+2$, $2+1+1$, and $1+1+1+1$.
\item $I$ is the incidence-total row that reads the quotient-level and codon-level totals from the displayed specialization.
\item $T$ records the downstream defect-flow handoff to the partition skeleton and incidence certificate.
\item $H$ records componentwise $\hsame$ transport for block sizes, legal decorations, defect exponents, product rows, specialization rows, incidence rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay through $M,S,D,E,F,Q,I,T,H$.
\item $P$ is the $\Pkg$ provenance over $\PartitionBasinPolynomialUp$, $\PartitionUp$, $\DefectFlowPartitionSkeletonUp$, $\PartitionCoreIncidenceCertificateUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PartitionBasinPolynomialUp}$ row.
\end{enumerate}
The carrier has no coordinate for a stochastic biology model, a host polynomial oracle, a quotient-semantic equality, an unbounded partition enumeration, or a hidden recurrence outside the displayed finite rows.
\end{definition}

\begin{theorem}[PartitionBasinPolynomial NameCert obligations]
\label{thm:partition-basin-polynomial-namecert-obligations}
For every accepted $\PartitionBasinPolynomialUp$ carrier
$$
B=(M,S,D,E,F,Q,I,T,H,C,P,N),
$$
the local $\NameCert_{\PartitionBasinPolynomialUp}$ surface consists exactly of block-count and block-size admission through $M,S$, legal-decoration admission through $D$, defect-exponent admission through $E$, product-formula exposure through $F$, four-coordinate specialization through $Q$, incidence-total readback through $I$, defect-flow handoff through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:partition-basin-polynomial-carrier}. The block-count and block-size rows supply the finite partition core on which the enumeration is read.

The decoration and defect rows are then exposed coordinatewise. For block $i$, the all-decoration contribution is $(1+q)^{(m-1)s_{i}}$, and the excluded no-private-coordinate contribution is $\left((1+q)^{m-1}-1\right)^{s_{i}}$.

Multiplying the legal block rows gives the product row $F$. The specialization row $Q$ evaluates the same finite formula on the five four-coordinate partition types, and the incidence row $I$ sums the displayed rows with their finite multiplicities.

Finally $T,H,C,P,N$ route the same polynomial surface to the defect-flow and incidence packets. Because no excluded stochastic, host-oracle, quotient-semantic, unbounded-enumeration, or hidden-recurrence coordinate occurs in the carrier, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[PartitionBasinPolynomial product specialization]
\label{thm:partition-basin-polynomial-product-specialization}
Every defect-flow consumer of an accepted $\PartitionBasinPolynomialUp$ carrier receives the product formula row for $\mathcal{B}_{P}(q)$ and the four-coordinate specialization row before reading quotient-level or codon-level incidence totals. The consumer sees only finite block-size, decoration, defect, product, specialization, incidence, transport, replay, provenance, and local NameCert rows.
\end{theorem}
\begin{proof}
Start from the obligations of \autoref{thm:partition-basin-polynomial-namecert-obligations}. They force the block-size ledger and legal-decoration rows to be displayed before the product formula can be consumed.

The four-coordinate row is a finite specialization of the same product row. Its incidence totals are read only after the partition types and finite multiplicities have been displayed.

The handoff through $T,H,C,P,N$ preserves the same finite surface for the defect-flow skeleton and partition-core incidence certificate. Thus no stochastic model, host generating-function oracle, quotient-semantic equality, or hidden enumeration can be read from the packet.
\end{proof}

\closureat{PartitionBasinPolynomialUp}{seedStr}

\begin{closurestatus}{\PartitionBasinPolynomialUp}
  \constructivestory{A $\PartitionBasinPolynomialUp$ packet is generated from block-count rows, block-size ledgers, legal-decoration rows, defect-exponent ledgers, a product-formula row, a four-coordinate specialization row, incidence-total rows, a defect-flow handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:partition-basin-polynomial-carrier}, \autoref{thm:partition-basin-polynomial-namecert-obligations}, and \autoref{thm:partition-basin-polynomial-product-specialization} seed the finite partition-basin polynomial packet over displayed block-size, decoration, defect, product, specialization, incidence, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a stochastic biology model, host generating-function oracle, quotient-level semantic equality, unbounded partition enumeration, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, product-formula exposure, four-coordinate specialization, incidence readback, transport, replay, provenance, and local naming for BEDC.Derived.PartitionBasinPolynomialUp.}
\end{closurestatus}
