\chapter{A Concrete Naming Certificate for $\CellularCarrierSwitchCostUp$}
\label{ch:concrete-instances-cellular-carrier-switch-cost-namecert}
\origin{ai}

The $\CellularCarrierSwitchCostUp$ packet realizes the carrier-switch audit surface of \autoref{ch:visions-cellular-substrate-as-carrier-alternative} as finite BEDC data. It sits beside the carrier encoding of \autoref{ch:concrete-instances-cellularcarrierencoding-namecert}, the BHist cell-row embedding of \autoref{ch:concrete-instances-bhist-cell-row-embedding-namecert}, the substrate classifier of \autoref{ch:concrete-instances-cellularsubstrateclassifier-namecert}, the cellular window trace of \autoref{ch:concrete-instances-cellular-window-trace-namecert}, and the carrier comparison of \autoref{ch:concrete-instances-cellular-carrier-bhist-equivalence-namecert}. The packet names the finite cost of retargeting theorem families, kernel verbs, proof scripts, and audit gates to a cellular carrier; it is not a replacement kernel carrier.

\begin{definition}[Cellular carrier switch-cost carrier]
\label{def:cellular-carrier-switch-cost-carrier}
A $\CellularCarrierSwitchCostUp$ carrier is a finite $\BHist$ packet
$$
S=(B,O,V,R,A,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the BHist theorem-family row, listing the finite family of BHist-facing statements under inspection.
\item $O$ is the cellular orbit row, exposing the finite cellular rows and orbit windows to which the statements would be retargeted.
\item $V$ is the verb-realignment row, recording how Mark, Hist, Ext, and Cont reads are translated to cellular classifier, orbit, extension, and continuation reads.
\item $R$ is the proof-retarget budget row, recording the displayed proof obligations that must be rebuilt after the carrier change.
\item $A$ is the audit-regeneration ledger, listing the checks that must be regenerated for the cellular statements and their NameCert markers.
\item $K$ is the non-escape row, recording that the packet measures the switch cost without replacing the public BEDC $\BHist$ carrier.
\item $H$ records componentwise $\hsame$ transport for theorem-family, orbit, verb, proof-budget, audit, non-escape, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through $B,O,V,R,A,K$ before any switch-cost read reaches the local certificate.
\item $P$ is the $\Pkg$ provenance over $\CellularCarrierSwitchCostUp$, $\CellularCarrierEncodingUp$, $\BHistCellRowEmbeddingUp$, $\CellularSubstrateClassifierUp$, $\CellularWindowTraceUp$, $\CellularVerbRealignmentUp$, $\CellularCarrierBHistEquivalenceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CellularCarrierSwitchCostUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,O,V,R,A,K,H,C,P,N$. It has no coordinate for a kernel-carrier replacement, infinite cellular semantics, host evaluator equivalence, hidden proof synthesis, or an audit gate outside the displayed ledger.
\end{definition}

\begin{theorem}[Cellular carrier switch-cost NameCert obligations]
\label{thm:cellular-carrier-switch-cost-namecert-obligations}
For every accepted $\CellularCarrierSwitchCostUp$ carrier $S=(B,O,V,R,A,K,H,C,P,N)$, the local $\NameCert_{\CellularCarrierSwitchCostUp}$ surface consists exactly of carrier admission, BHist theorem-family exposure, cellular orbit exposure, verb realignment, proof-retarget budgeting, audit-regeneration accounting, non-escape, transport, replay, provenance, and local naming obligations. A valid switch-cost read must display both the proof-retarget budget row $R$ and the audit-regeneration ledger $A$ before it reaches the local certificate.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cellular-carrier-switch-cost-carrier}. The rows $B$ and $O$ expose the two carriers being compared as finite theorem-family and orbit-window data.

The verb row $V$ records the syntactic realignment of Mark, Hist, Ext, and Cont. It does not itself measure the engineering cost, because statement retargeting and proof rebuilding are separate rows.

The proof-retarget budget $R$ and audit-regeneration ledger $A$ are therefore mandatory. A packet omitting either row cannot certify the displayed switch cost, since it would hide either the proof obligations or the audit gates that must be regenerated.

Finally $K,H,C,P,N$ preserve the non-replacement boundary, replay the finite route, record provenance, and name the packet. No hidden carrier replacement, infinite orbit semantics, host evaluator equivalence, or external audit gate is available outside those rows.
\end{proof}

\begin{theorem}[Cellular carrier switch-cost finite audit route]
\label{thm:cellular-carrier-switch-cost-finite-audit-route}
Every accepted $\CellularCarrierSwitchCostUp$ read factors through the finite route
$$
B,O,V,R,A,K,H,C,P,N .
$$
The route measures a BHist theorem-family transposition by first displaying the theorem family, then the cellular orbit window, then the verb-realignment row, then the proof-retarget budget, and then the audit-regeneration ledger. It cannot export carrier replacement, host bisimulation, unbounded cellular traces, hidden proof repair, or completed audit success outside the displayed packet.
\end{theorem}
\begin{proof}
Read $B$ first to identify the theorem-family surface whose statements are being retargeted. Read $O$ next to expose the finite cellular orbit window available to the target carrier.

The row $V$ aligns the verbs but does not discharge the work. It only states which BHist reads correspond to which cellular classifier and orbit reads.

The rows $R$ and $A$ then carry the cost. Proof retargeting is visible in $R$, while audit regeneration is visible in $A$, so the packet measures both proof work and gate work before local naming.

The non-escape and structural rows $K,H,C,P,N$ keep this as a finite audit NameCert packet. Because no other coordinate exists, the route cannot export a carrier replacement, host bisimulation, unbounded trace, hidden proof repair, or completed audit success.
\end{proof}

\falsifiablePrediction{A valid $\CellularCarrierSwitchCostUp$ packet is refuted if it omits the proof-retarget budget row or the audit-regeneration ledger.}

\independenceWitness{cellularcarrierencoding, bhist-cell-row-embedding, cellularsubstrateclassifier, cellular-window-trace: $\CellularCarrierSwitchCostUp$ is not bijective to any listed sibling because it jointly carries BHist theorem-family, cellular orbit, verb-realignment, proof-retarget, audit-regeneration, non-escape, transport, replay, provenance, and local naming rows.}

Lean $\mathsf{TasteGate}$ coverage for this packet must provide $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances in $\mathsf{BEDC.Derived.CellularCarrierSwitchCostUp.TasteGate}$.

\closureat{CellularCarrierSwitchCostUp}{seedStr}

\begin{closurestatus}{\CellularCarrierSwitchCostUp}
  \constructivestory{A $\CellularCarrierSwitchCostUp$ packet is generated from BHist theorem-family rows, cellular orbit rows, verb-realignment rows, proof-retarget budget rows, audit-regeneration ledgers, non-escape rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cellular-carrier-switch-cost-carrier}, \autoref{thm:cellular-carrier-switch-cost-namecert-obligations}, and \autoref{thm:cellular-carrier-switch-cost-finite-audit-route} seed the finite audit object for cellular carrier-switch cost.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close kernel-carrier replacement, infinite cellular semantics, host evaluator equivalence, hidden proof synthesis, completed audit success, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, theorem-family exposure, cellular orbit exposure, verb realignment, proof-retarget budgeting, audit-regeneration accounting, non-escape, transport, replay, provenance, and local naming for BEDC.Derived.CellularCarrierSwitchCostUp.}
\end{closurestatus}
