\chapter{A Concrete Naming Certificate for $\BishopCauchyRepresentationComparisonUp$}
\label{ch:concrete-instances-bishop-cauchy-representation-comparison-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopCauchyRepresentationComparisonUp$ packet records the finite comparison surface between Bishop-style Cauchy representations and the BEDC real-name ladder. It sits after the Cauchy-representation route of \autoref{ch:concrete-instances-cauchy-representation-namecert}, the precision ledger of \autoref{ch:concrete-instances-bishop-real-precision-namecert}, the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the comparison route as finite NameCert data; it is not quotient stream equality, selected host limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop Cauchy representation comparison carrier]
\label{def:bishop-cauchy-representation-comparison-carrier}
A $\BishopCauchyRepresentationComparisonUp$ carrier is a finite $\BHist$ packet
$$
K=(R,B,S,Q,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\CauchyRepresentationUp$ row whose decoder route supplies the representation-facing observations.
\item $B$ is the $\BishopRealPrecisionUp$ row recording the requested constructive precision discipline for the comparison.
\item $S$ is the $\StreamNameUp$ finite-window row shared by the representation and precision reads.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the displayed stream windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by the precision and regular-readback rows.
\item $E$ is the terminal $\RealUp$ seal reached only after $R,B,S,Q,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the representation row, precision row, stream windows, regular readback, dyadic ledger, terminal seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a comparison request through $R,B,S,Q,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopCauchyRepresentationComparisonUp$, $\CauchyRepresentationUp$, $\BishopRealPrecisionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCauchyRepresentationComparisonUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite comparison packet. It has no coordinate for quotient streams, selected limits, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop Cauchy representation comparison NameCert obligations]
\label{thm:bishop-cauchy-representation-comparison-namecert-obligations}
For every accepted $\BishopCauchyRepresentationComparisonUp$ carrier $K=(R,B,S,Q,D,E,H,C,P,N)$, the local $\NameCert_{\BishopCauchyRepresentationComparisonUp}$ surface consists exactly of carrier admission for the displayed packet, representation decoding through $R$, constructive precision exposure through $B$, shared finite-window access through $S$, regular rational readback through $Q$, dyadic tolerance accounting through $D$, terminal real-name sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The visible analytic data are the representation decoder $R$, precision row $B$, shared stream window $S$, regular rational readback $Q$, dyadic tolerance ledger $D$, and terminal real seal $E$.

The comparison obligations are componentwise. A representation-facing consumer first reads $R$, then the requested Bishop precision surface $B$, and then the common finite-window, regular-readback, and dyadic-tolerance route $S,Q,D$.

Only after these rows are displayed may the consumer inspect the terminal seal $E$. The support rows $H,C,P,N$ transport, replay, source, and name the same finite route, so no further NameCert obligation remains outside the listed coordinates.
\end{proof}

\begin{theorem}[Bishop Cauchy representation comparison nonescape]
\label{thm:bishop-cauchy-representation-comparison-nonescape}
No accepted $\BishopCauchyRepresentationComparisonUp$ carrier exports quotient streams, selected host limits, countable choice, trichotomy, host real equality, or ambient $\RealUp$ completeness. Every downstream Real or Completion consumer receives only the displayed representation row, Bishop precision row, stream-window row, regular readback row, dyadic tolerance ledger, terminal real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row.
\end{theorem}
\begin{proof}
Inspect the carrier inventory. The tuple contains only $R,B,S,Q,D,E,H,C,P,N$.

The rows $R,B,S,Q,D$ are the complete comparison route before the terminal Real seal can be consumed. Thus the seal $E$ is not a selected host limit; it is the downstream endpoint of the displayed representation, precision, window, readback, and tolerance data.

Transport, replay, provenance, and local naming preserve the same boundary. Since no coordinate stores quotient stream equality, a choice schedule, a trichotomy branch, host real equality, or an ambient completeness principle, none can escape from the packet.
\end{proof}

\closureat{BishopCauchyRepresentationComparisonUp}{seedStr}

\begin{closurestatus}{\BishopCauchyRepresentationComparisonUp}
  \constructivestory{A $\BishopCauchyRepresentationComparisonUp$ packet is generated from a CauchyRepresentation decoder, a BishopRealPrecision row, a StreamName finite window, a RegSeqRat readback row, a DyadicRatCore tolerance ledger, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-cauchy-representation-comparison-carrier}, \autoref{thm:bishop-cauchy-representation-comparison-namecert-obligations}, and \autoref{thm:bishop-cauchy-representation-comparison-nonescape} seed the finite representation-comparison route from CauchyRepresentation and BishopRealPrecision data to StreamName, RegSeqRat, DyadicRatCore, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, representation-decoder exactness, precision-row exposure, shared-window readback, dyadic tolerance accounting, Real seal ordering, transport, replay, provenance, and local naming for BEDC.Derived.BishopCauchyRepresentationComparisonUp.}
\end{closurestatus}
