\chapter{A Concrete Naming Certificate for $\HoeffdingFiniteSumUp$}
\label{ch:concrete-instances-hoeffding-finite-sum-namecert}
\origin{human}

Following Hoeffding's finite bounded-sum inequality, the $\HoeffdingFiniteSumUp$ packet records the finite concentration route by which independent bounded random variables yield an exponential tail estimate. It sits after the probability source of \autoref{ch:concrete-instances-probspace-namecert}, the measurable random-variable rows of \autoref{ch:concrete-instances-randomvar-namecert}, the law and range summaries of \autoref{ch:concrete-instances-distribution-namecert}, the independence ledger of \autoref{ch:concrete-instances-independence-namecert}, the dyadic exponential-bound arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal seal of \autoref{ch:concrete-instances-real-namecert}, and the finite-average probability route of \autoref{ch:concrete-instances-weak-law-large-numbers-namecert}. The packet names a bounded finite-sum concentration certificate; it is not a martingale inequality, a Chernoff optimization principle, an almost-sure convergence theorem, a host measure-theoretic limit, or an ambient $\RealUp$ completeness result.

\begin{definition}[Hoeffding finite-sum carrier]\label{def:hoeffding-finite-sum-carrier}
A $\HoeffdingFiniteSumUp$ carrier is a finite $\BHist$ packet
$$
(P,V,I,B,S,D,E,H,C,Q,N).
$$
Here $P$ is the source $\ProbSpaceUp$ row carrying the event classifier and total-mass normalization. The row $V$ is the finite family of $\RandomVarUp$ entries read over $P$. The row $I$ is the $\IndependenceUp$ ledger certifying that the displayed family is independent in the finite index range under inspection. The row $B$ is the bounded-range ledger: for each displayed variable it records lower and upper $\RealUp$ seals and the corresponding $\DistributionUp$ range summary. The row $S$ records the centered finite-sum expression and the positive deviation request. The row $D$ is the $\DyadicRatCoreUp$ exponential-bound row naming the finite dyadic numerator, denominator, square, range-width sum, and slack comparison used by the displayed Hoeffding bound. The row $E$ is the terminal $\RealUp$ tail seal naming the probability estimate for the exceptional event. The row $H$ records componentwise $\hsame$ transport, $C$ records $\Cont$ replay of the finite concentration route, $Q$ records $\Pkg$ provenance over $\ProbSpaceUp$, $\RandomVarUp$, $\IndependenceUp$, $\DistributionUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$, and $N$ is the local $\NameCert_{\HoeffdingFiniteSumUp}$ row. The classifier compares accepted carriers only through these eleven rows.
\end{definition}

\begin{theorem}[Hoeffding finite-sum NameCert obligations]\label{thm:hoeffding-finite-sum-namecert-obligations}
For every accepted $\HoeffdingFiniteSumUp$ carrier $(P,V,I,B,S,D,E,H,C,Q,N)$, the local $\NameCert_{\HoeffdingFiniteSumUp}$ surface consists exactly of the finite rows in \autoref{def:hoeffding-finite-sum-carrier}. Carrier admission displays the probability source, finite random-variable family, independence ledger, bounded-range ledger, finite-sum row, dyadic exponential-bound row, $\RealUp$ tail seal, transport, replay, provenance, and local naming row. The certificate imports no host concentration theorem, martingale filtration, Chernoff variational optimizer, countable-choice schedule, external probability-limit operation, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Read the carrier rows in order. The source row $P$ supplies the event classifier and normalization, while $V$ exposes only a finite family of random variables over that same probability source.

The independence row $I$ and bounded-range row $B$ are then finite ledgers. They state exactly which variables are independent and which displayed lower and upper seals bound each variable before any exponential estimate is available.

The finite-sum row $S$ fixes the centered sum and requested deviation. The dyadic row $D$ records the arithmetic denominator, squared deviation, accumulated range-width budget, and slack comparison used by the exponential estimate, and the $\RealUp$ row $E$ seals the resulting tail bound.

Finally $H,C,Q,N$ transport, replay, source, and name the same route. Since the carrier has no coordinate for a host concentration theorem, variational optimizer, infinite limit, or completeness principle, these displayed rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Hoeffding finite tail-bound route]\label{thm:hoeffding-finite-sum-tail-bound-route}
Every accepted $\HoeffdingFiniteSumUp$ tail-bound read factors through the route
$$
\ProbSpaceUp,\ \RandomVarUp,\ \IndependenceUp,\ \DistributionUp,\ \DyadicRatCoreUp \longmapsto \RealUp
$$
as displayed by the carrier rows $P,V,I,B,S,D,E,H,C,Q,N$. A probability-bound consumer can inspect the exceptional-event estimate only after the finite probability source, random-variable family, independence ledger, bounded-range ledger, centered-sum row, dyadic exponential-bound row, terminal real seal, transport, replay, provenance, and local naming row have been displayed.
\end{theorem}
\begin{proof}
Start with an accepted carrier and project the source rows. The probability source $P$ and finite random-variable family $V$ provide the only measurable data available to the tail-bound request.

Next read $I$ and $B$. The independence ledger is the only route by which the product-event step enters the packet, and the bounded-range ledger is the only route by which distributional lower and upper seals enter the range-width budget.

The centered-sum row $S$ then determines the finite event being bounded. The dyadic row $D$ supplies the exponential-bound arithmetic for that event, and the $\RealUp$ seal $E$ is downstream from the same displayed dyadic comparison.

The structural rows $H,C,Q,N$ preserve that route under classifier replacement and local naming. Therefore every tail-bound read is the finite Hoeffding handoff itself, not a hidden appeal to an external concentration theorem or ambient real-completeness principle.
\end{proof}

\begin{theorem}[Hoeffding finite-sum nonescape]\label{thm:hoeffding-finite-sum-nonescape}
For every accepted $\HoeffdingFiniteSumUp$ packet, every concentration-facing read remains inside the displayed rows $P,V,I,B,S,D,E,H,C,Q,N$. In particular, the packet exports no martingale filtration, Chernoff optimizer, almost-sure convergence claim, host probability-limit operator, countable-choice selection, quotient equality of real names, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:hoeffding-finite-sum-carrier} has no coordinate beyond the eleven displayed rows. Thus a concentration-facing request can only project the probability source, finite variables, independence ledger, range ledger, sum row, dyadic estimate, real tail seal, transport, replay, provenance, and local name.

The analytic content of the request is concentrated in $I,B,S,D,E$. Independence, bounded ranges, the finite centered sum, dyadic exponential arithmetic, and the terminal tail seal appear as explicit rows, so no further theorem object can be read from the packet.

The remaining rows $H,C,Q,N$ are structural. They preserve displayed histories, replay the finite route, record package provenance, and attach the local certificate. Hence the accepted packet cannot export any of the excluded limit, optimizer, quotient, choice, or completeness principles.
\end{proof}

\begin{closurestatus}{\HoeffdingFiniteSumUp}
  \constructivestory{A $\HoeffdingFiniteSumUp$ packet is generated from a probability source row, finite random-variable family, independence ledger, bounded-range ledger, centered finite-sum row, dyadic exponential-bound row, RealUp tail seal, componentwise hsame transport, continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hoeffding-finite-sum-carrier}, \autoref{thm:hoeffding-finite-sum-namecert-obligations}, \autoref{thm:hoeffding-finite-sum-tail-bound-route}, and \autoref{thm:hoeffding-finite-sum-nonescape} seed the bounded finite-sum concentration route through ProbSpace, RandomVar, Independence, Distribution, DyadicRatCore, RealUp, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close martingale inequalities, Chernoff optimization, almost-sure convergence, host probability limits, countable-choice selection, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite independence routing, bounded-range stability, dyadic exponential-bound handoff, tail-seal nonescape, transport, replay, provenance, and local naming for future BEDC.Derived.HoeffdingFiniteSumUp.}
\end{closurestatus}
