\chapter{A Concrete Naming Certificate for $\CauchyModulusBridgeUp$}
\label{ch:concrete-instances-cauchy-modulus-bridge-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CauchyModulusBridgeUp$ packet records the finite handoff by which a displayed Cauchy-criterion request becomes an explicit modulus schedule before any regular-rational readback or real-name seal is consumed. It sits after the effective criterion packet of \autoref{ch:concrete-instances-effective-cauchy-criterion-namecert}, the modulus schedule surface of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the L10 bridge from criterion-facing reads to explicit schedules as finite NameCert data; it is not quotient stream equality, a selected host limit, countable choice, trichotomy, host sequence equality, or ambient $\RealUp$ completeness.

\begin{definition}[Cauchy modulus bridge carrier]
\label{def:cauchy-modulus-bridge-carrier}
A $\CauchyModulusBridgeUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,M,E,S,D,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\CauchyCriterionUp$ request row naming the late-pair comparison surface to be served by the bridge.
\item $M$ is the $\CauchyModulusUp$ schedule row assigning the displayed precision request to a finite tail threshold.
\item $E$ is the $\mathsf{EffectiveCauchyCriterion}^{\uparrow}$ row tying the same criterion request and modulus schedule to a finite effective handoff.
\item $S$ is the $\StreamNameUp$ finite-window row opened by the criterion request and scheduled by the modulus row.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the radius, tail comparison, and endpoint budget used by the request.
\item $R$ is the $\RegSeqRatUp$ readback row available only after $Q,M,E,S,D$ have been displayed.
\item $L$ is the terminal $\RealUp$ seal row available only after the criterion, modulus, effective handoff, window, tolerance, and regular-rational rows have been read.
\item $H$ records componentwise $\hsame$ transport for the criterion, modulus, effective handoff, stream-window, dyadic, regular-rational, real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Cauchy-criterion request through $Q,M,E,S,D,R,L,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyModulusBridgeUp$, $\CauchyCriterionUp$, $\CauchyModulusUp$, $\mathsf{EffectiveCauchyCriterion}^{\uparrow}$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyModulusBridgeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,M,E,S,D,R,L,H,C,P,N$. It has no coordinate for quotient streams, selected limits, host sequence equality, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy modulus bridge NameCert obligations]
\label{thm:cauchy-modulus-bridge-namecert-obligations}
For every accepted $\CauchyModulusBridgeUp$ carrier $B=(Q,M,E,S,D,R,L,H,C,P,N)$, the local $\NameCert_{\CauchyModulusBridgeUp}$ surface consists exactly of carrier admission for the displayed criterion row $Q$, modulus schedule $M$, effective criterion handoff $E$, finite stream window $S$, dyadic tolerance ledger $D$, regular-rational readback $R$, terminal real seal $L$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-modulus-bridge-carrier}. The analytic rows visible to a consumer are exactly the criterion request $Q$, modulus schedule $M$, effective handoff $E$, finite window $S$, dyadic tolerance ledger $D$, regular-rational readback $R$, and terminal real seal $L$.

The bridge obligation is the ordering of those rows. A Cauchy-criterion request first exposes $Q$ and then reads the displayed threshold in $M$ through the effective handoff $E$; only after that handoff are the stream window $S$ and dyadic tolerance ledger $D$ available for regular readback.

The downstream rows are forced by the same carrier projection. The row $R$ is the $\RegSeqRatUp$ readback obtained from the displayed window and tolerance data, and $L$ is the $\RealUp$ seal reached only through that readback.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no excluded coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy modulus bridge effective-criterion handoff]
\label{thm:cauchy-modulus-bridge-effective-criterion-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\CauchyModulusBridgeUp$ packet factors through the finite route
$$
\CauchyCriterionUp \longmapsto \CauchyModulusUp \longmapsto \mathsf{EffectiveCauchyCriterion}^{\uparrow} \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The handoff exposes only the displayed criterion request, explicit modulus schedule, effective criterion row, finite stream window, dyadic tolerance ledger, regular rational readback, terminal real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows. It exports no quotient stream equality, selected host limit, hidden modulus oracle, countable-choice schedule, trichotomy split, host sequence equality, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:cauchy-modulus-bridge-namecert-obligations}. It places every consumer read behind the criterion row, the explicit modulus row, and the effective criterion handoff.

Next open the finite observation route. The stream-window row $S$ and dyadic tolerance row $D$ are downstream of $Q,M,E$, so the regular-rational row $R$ is a displayed readback from the same request rather than a detached sequence or selected limit.

The terminal seal is last. The $\RealUp$ row $L$ is consumed only after $R$ has been displayed, while $H,C,P,N$ preserve the same dependency order under transport, replay, provenance, and local naming.

Thus any $\RegSeqRatUp$ or $\RealUp$ consumer sees exactly the route stated in the theorem and cannot bypass it through a hidden analytic object.
\end{proof}

\closureat{CauchyModulusBridgeUp}{seedStr}

\begin{closurestatus}{\CauchyModulusBridgeUp}
  \constructivestory{A $\CauchyModulusBridgeUp$ packet is generated from a CauchyCriterion request row, a CauchyModulus schedule, an effective Cauchy criterion handoff, finite StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-modulus-bridge-carrier}, \autoref{thm:cauchy-modulus-bridge-namecert-obligations}, and \autoref{thm:cauchy-modulus-bridge-effective-criterion-handoff} seed the finite bridge from Cauchy-criterion requests to explicit modulus schedules before RegSeqRat and Real consumers read the route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, hidden modulus oracles, countable choice, trichotomy, host sequence equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, criterion-to-modulus exactness, effective handoff ordering, StreamName and DyadicRatCore readback, RegSeqRat handoff, RealUp seal confinement, transport stability, continuation replay, and provenance nonescape for BEDC.Derived.CauchyModulusBridgeUp.}
\end{closurestatus}
