\chapter{A Concrete Naming Certificate for $\HausdorffMeasureUp$}
\label{ch:concrete-instances-hausdorff-measure-namecert}
\origin{human}

Following Hausdorff and Federer's metric measure theory, the $\HausdorffMeasureUp$ packet records the finite dyadic-cover surface through which Hausdorff content and scale-stable measure reads become visible inside BEDC. It sits over the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the cover-valued outer-measure boundary of \autoref{ch:concrete-instances-outer-measure-namecert}, and the finite scale-cover comparison surface of \autoref{ch:concrete-instances-box-dimension-namecert}. The packet names only displayed dyadic cover packets, diameter budgets, weighted cover sums, scale comparison, transport, replay, provenance, and local naming; it is not a quotient cover family, not a selected infimum, not countable choice over covers, and not an ambient measure primitive.

\begin{definition}[Hausdorff measure dyadic-cover carrier]
\label{def:hausdorff-measure-carrier}
A $\HausdorffMeasureUp$ carrier is a finite $\BHist$ packet
$$
H=(M,D,R,O,B,C,S,T,E,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricUp$ source row, exposing the finite point classifier and distance comparisons used to bound cover diameters.
\item $D$ is the $\DyadicRatCoreUp$ scale row, naming the dyadic radius budget and dyadic exponent used by the cover packet.
\item $R$ is the $\RealUp$ value-seal row for diameter powers and finite cover sums.
\item $O$ is the $\OuterMeasureUp$ handoff row, read only as a finite cover-valued boundary and not as a completed measure primitive.
\item $B$ is the $\BoxDimensionUp$ comparison row, exposing finite scale-cover counts against the same dyadic scale.
\item $C$ is the finite dyadic cover packet, listing the displayed cover cells, their metric diameter witnesses, and their membership reads.
\item $S$ is the cover-sum ledger, recording the finite Real-sealed sum of dyadic diameter weights.
\item $T$ is the scale-stability ledger, recording that dyadic refinement reads the same metric source, outer-measure boundary, and box-dimension comparison rows.
\item $E$ records componentwise $\hsame$ transport for metric, dyadic scale, Real seal, outer-measure handoff, box-dimension comparison, cover packet, cover sum, and stability rows.
\item $K$ records displayed $\Cont$ replay from a metric source and dyadic scale through $C,S,T,E,P,N$.
\item $P$ is the $\Pkg$ provenance over $\HausdorffMeasureUp$, $\MetricUp$, $\DyadicRatCoreUp$, $\RealUp$, $\OuterMeasureUp$, $\BoxDimensionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HausdorffMeasureUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,D,R,O,B,C,S,T,E,K,P,N$. It has no coordinate for quotient cover families, selected infima, countable-choice schedules over covers, host sigma-algebras, or ambient measure primitives.
\end{definition}

\begin{theorem}[Hausdorff measure NameCert obligations]
\label{thm:hausdorff-measure-namecert-obligations}
For every accepted $\HausdorffMeasureUp$ carrier $H=(M,D,R,O,B,C,S,T,E,K,P,N)$, the local $\NameCert_{\HausdorffMeasureUp}$ surface consists exactly of metric source admission, dyadic scale exposure, Real value sealing, finite outer-measure handoff, box-dimension scale comparison, finite dyadic cover admission, cover-sum exactness, scale-stability replay, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every measure-facing or dimension-facing consumer must read the displayed route
$$
\MetricUp,\DyadicRatCoreUp,\RealUp \longmapsto C,S,T \longmapsto \OuterMeasureUp,\BoxDimensionUp \longmapsto E,K,P,N
$$
before treating the packet as a Hausdorff-measure read.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hausdorff-measure-carrier}. The metric row $M$, dyadic row $D$, and Real seal row $R$ are the only sources for distances, scales, and finite value readback.

The cover packet $C$ and cover-sum ledger $S$ are finite rows. They record displayed cover cells and dyadic diameter weights, so no step selects a minimizing cover family or takes an external infimum.

The outer-measure and box-dimension rows $O,B$ are downstream comparison boundaries. They can read the same finite cover data, but they do not add a completed host measure, a quotient of covers, or countable choice over refinements.

Finally $T,E,K,P,N$ transport, replay, source, and name the same finite route. Since every exported obligation is one of the listed rows, the local classifier cannot expose an ambient measure primitive or any detached cover selector.
\end{proof}

\begin{theorem}[Hausdorff measure dyadic-cover stability]
\label{thm:hausdorff-measure-dyadic-cover-stability}
Let $H=(M,D,R,O,B,C,S,T,E,K,P,N)$ be an accepted $\HausdorffMeasureUp$ carrier. For any displayed dyadic refinement of the scale row $D$, the scale-stability ledger $T$ forces the refined read to reuse the same $\MetricUp$ source, the same $\RealUp$ value-seal route, the same finite $\OuterMeasureUp$ cover boundary, and the same $\BoxDimensionUp$ scale-count comparison before any consumer reads a Hausdorff-measure claim. The stable route is
$$
M,D,R,C,S,T \longmapsto O,B \longmapsto E,K,P,N .
$$
It exports no quotient cover family, selected infimum, countable-choice cover schedule, host sigma-algebra closure, or ambient measure primitive.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:hausdorff-measure-carrier}. A dyadic refinement changes only the displayed scale request inside $D$ and the finite cover packet admitted by $C$.

Use the stability ledger $T$. It records that the refined cover is replayed against the same metric source and that its finite cover sum is sealed through the same Real row, so the refinement cannot introduce a detached minimizing cover or a host infimum.

The comparison rows $O$ and $B$ then read the refined packet as finite outer-measure and box-dimension boundary data. Componentwise transport and displayed replay through $E,K,P,N$ preserve that route, while quotient covers, countable choice, host sigma-algebras, and ambient measure primitives remain absent from the carrier.
\end{proof}

\falsifiablePrediction{An accepted $\HausdorffMeasureUp$ consumer that reaches a Hausdorff-measure read without first exposing a MetricUp source row, a DyadicRatCore scale row, a RealUp value seal, a finite dyadic cover packet, a finite cover-sum ledger, an OuterMeasureUp handoff, a BoxDimensionUp comparison row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row refutes the carrier surface.}

\independenceWitness{metric, dyadicratcore, real, outermeasure, boxdimension: $\HausdorffMeasureUp$ is not bijective to any listed sibling because it binds metric diameter data, dyadic scales, Real-sealed finite cover sums, outer-measure cover boundaries, and box-dimension scale counts into one finite cover-stability NameCert packet.}

\closureat{HausdorffMeasureUp}{seedStr}

\begin{closurestatus}{\HausdorffMeasureUp}
  \constructivestory{A $\HausdorffMeasureUp$ packet is generated from a MetricUp source row, DyadicRatCore scale row, RealUp value-seal row, finite OuterMeasureUp handoff, BoxDimensionUp comparison row, finite dyadic cover packet, cover-sum ledger, scale-stability ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-measure-carrier}, \autoref{thm:hausdorff-measure-namecert-obligations}, and \autoref{thm:hausdorff-measure-dyadic-cover-stability} seed the finite dyadic-cover Hausdorff-measure interface over MetricUp, DyadicRatCoreUp, RealUp, OuterMeasureUp, and BoxDimensionUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient cover families, selected infima, countable choice over covers, host sigma-algebra completion, ambient measure primitives, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic scale exposure, finite cover admission, cover-sum exactness, scale-stability replay, outer-measure handoff, box-dimension comparison, transport, provenance, and no-escape for BEDC.Derived.HausdorffMeasureUp.}
\end{closurestatus}
