\chapter{A Concrete Naming Certificate for $\PartitionBasinUp$}
\label{ch:concrete-instances-partition-basin-namecert}
\origin{human}

Following finite partition enumeration, the $\PartitionBasinUp$ packet records the partition-core basin counts of \autoref{thm:philosophy-partition-basin-size} as concrete NameCert data over finite block ledgers, legal decoration rows, product-count readback, incidence totals, transport, replay, provenance, and local naming. It sits over the $\PartitionUp$ carrier of \autoref{ch:concrete-instances-partition-namecert}, the $\NatUp$ and $\ListUp$ finite row spine used there, and the polynomial refinement of \autoref{ch:concrete-instances-partition-basin-polynomial-namecert}. The packet names finite counting data; it is not a stochastic biology model, a host enumeration oracle, a quotient-semantic equality, or an unbounded recurrence.

\begin{definition}[PartitionBasin carrier]
\label{def:partition-basin-carrier}
A $\PartitionBasinUp$ carrier is a finite $\BHist$ packet
$$
B=(P,M,S,D,F,I,T,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the accepted $\PartitionUp$ core row, read through $\ListUp$ and $\NatUp$ positive-part data.
\item $M$ is the block-count row for the finite partition core.
\item $S$ is the block-size ledger $(s_{1},\ldots,s_{m})$ attached to $P$.
\item $D$ is the legal decoration row: for a coordinate in block $i$, the row records the admissible subsets of the other $m-1$ blocks and the private-coordinate exclusion for that block.
\item $F$ is the finite product-count row
$$
\prod_{i=1}^{m}
\left(
(2^{m-1})^{s_{i}}
-
(2^{m-1}-1)^{s_{i}}
\right).
$$
\item $I$ is the incidence-total readback row, including the quotient-level basin count and the finite lift count used by codon-level consumers.
\item $T$ is the downstream handoff row to $\PartitionBasinPolynomialUp$ and to finite defect-flow consumers that need the same basin surface.
\item $H$ records componentwise $\hsame$ transport for partition, block-count, block-size, decoration, product-count, incidence, handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through $P,M,S,D,F,I,T,H$.
\item $Q$ is the $\Pkg$ provenance over $\PartitionBasinUp$, $\PartitionUp$, $\PartitionBasinPolynomialUp$, $\ListUp$, $\NatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PartitionBasinUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed finite partition, block, decoration, product, incidence, transport, replay, provenance, and local naming rows.
\end{definition}

\begin{theorem}[PartitionBasin NameCert obligations]
\label{thm:partition-basin-namecert-obligations}
For every accepted $\PartitionBasinUp$ carrier
$$
B=(P,M,S,D,F,I,T,H,C,Q,N),
$$
the local $\NameCert_{\PartitionBasinUp}$ surface consists exactly of partition-core admission through $P$, finite block-count admission through $M$, block-size readback through $S$, legal-decoration admission through $D$, product-count exposure through $F$, incidence-total readback through $I$, downstream handoff through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $Q$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:partition-basin-carrier}. The partition core is already finite because $P$ is an accepted $\PartitionUp$ row over $\ListUp$ and $\NatUp$ data, and the block-count and block-size rows are read from that finite core.

For each block $i$, the decoration row $D$ lists the admissible subsets of the other $m-1$ blocks. The private-coordinate exclusion removes the all-nonprivate case, so the legal block contribution is $(2^{m-1})^{s_i}-(2^{m-1}-1)^{s_i}$.

Multiplying the displayed block contributions gives $F$, and the incidence row $I$ reads quotient-level and finite-lift totals from the same product-count surface. The remaining rows $T,H,C,Q,N$ transport, replay, source, and name that finite surface without adding a host enumeration oracle, quotient-semantic equality, stochastic model, or hidden recurrence.
\end{proof}

\closureat{PartitionBasinUp}{seedStr}

\begin{closurestatus}{\PartitionBasinUp}
  \constructivestory{A $\PartitionBasinUp$ packet is generated from a PartitionUp core row, finite NatUp block-count rows, ListUp block-size ledgers, legal decoration rows, product-count rows, incidence-total readback, downstream handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:partition-basin-carrier} and \autoref{thm:partition-basin-namecert-obligations} seed the finite partition-basin counting packet over displayed partition, block-count, block-size, decoration, product, incidence, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a stochastic biology model, host enumeration oracle, quotient-level semantic equality, unbounded partition enumeration, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite block readback, legal-decoration exposure, product-count exactness, incidence readback, transport, replay, provenance, and local naming for BEDC.Derived.PartitionBasinUp.}
\end{closurestatus}
