\chapter{A Concrete Naming Certificate for $\CompletionModulusCategoryUp$}
\label{ch:concrete-instances-completion-modulus-category-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and the functorial treatment of completions, the $\CompletionModulusCategoryUp$ packet records the finite category surface whose arrows preserve displayed completion moduli. It sits after the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the completion functor of \autoref{ch:concrete-instances-completionfunctor-namecert}, and the Cauchy completion functor of \autoref{ch:concrete-instances-cauchycompletionfunctor-namecert}. The packet names modulus-preserving completion morphisms as BEDC rows; it does not export quotient completions, selected representatives, host continuous maps, countable choice, or ambient completeness.

\begin{definition}[CompletionModulusCategory carrier]
\label{def:completion-modulus-category-carrier}
A $\CompletionModulusCategoryUp$ carrier is a finite $\BHist$ packet
$$
M=(O,A,S,R,D,E,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the object ledger. Each object row records a completion-facing source, its displayed Cauchy-modulus discipline, and the local completion target read through the surrounding completion chapters.
\item $A$ is the arrow ledger. Each arrow row records a finite morphism request together with the modulus transformation that sends source tolerances to target tolerances.
\item $S$ is the $\StreamNameUp$ finite-window row used to inspect the source and target names of an arrow.
\item $R$ is the $\RegSeqRatUp$ readback row reached after the stream windows have been displayed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare source and target moduli.
\item $E$ is the $\RealUp$ seal row read only after $S,R,D$ have supplied the displayed tolerance route.
\item $F$ records identity and composition rows for the completion functoriality surface, with identity arrows preserving the same modulus and composite arrows composing the displayed modulus transformations.
\item $H$ records componentwise $\hsame$ transport for object rows, arrow rows, stream windows, regular readback, dyadic tolerances, Real seals, functoriality rows, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an arrow request through $O,A,S,R,D,E,F,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CompletionModulusCategoryUp$, $\CompletionFunctorUp$, $\CauchyCompletionFunctorUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompletionModulusCategoryUp}$ row.
\end{enumerate}
The carrier predicate asserts exactly that these rows form one finite category packet for modulus-preserving completion morphisms. It has no coordinate for quotient completion points, selected representatives, host functions, global choice schedules, or ambient completeness.
\end{definition}

\begin{theorem}[CompletionModulusCategory NameCert obligations]
\label{thm:completion-modulus-category-namecert-obligations}
For every accepted $\CompletionModulusCategoryUp$ carrier $M=(O,A,S,R,D,E,F,H,C,P,N)$, the local $\NameCert_{\CompletionModulusCategoryUp}$ surface consists exactly of carrier admission for the displayed object ledger, arrow ledger, stream windows, regular rational readback, dyadic tolerance ledger, Real seal, identity and composition rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming row.

The obligation surface additionally requires each arrow row in $A$ to expose its source modulus, target modulus, and modulus transformation before any $\RealUp$-facing read is accepted; each identity row in $F$ to preserve the displayed modulus without adding a choice coordinate; and each composition row in $F$ to compose the two displayed modulus transformations before the downstream seal is visible.
\end{theorem}
\begin{proof}
Project the accepted carrier. The packet contains only the rows $O,A,S,R,D,E,F,H,C,P,N$, so carrier admission and ledger exhaustion are componentwise.

An arrow-facing request first reads the object and arrow ledgers $O,A$. The source and target names are then inspected through the finite stream windows $S$, regular rational readback $R$, and dyadic tolerance ledger $D$.

The functoriality rows $F$ are local to the same displayed moduli. Identity preserves the stored modulus transformation, and composition combines the two stored transformations before the terminal seal $E$ can be read.

Finally $H,C,P,N$ transport, replay, source, and name this same finite route. Since quotient completions, selected representatives, host functions, global choice schedules, and ambient completeness are not carrier coordinates, they cannot be exported by the local NameCert.
\end{proof}

\begin{theorem}[CompletionModulusCategory modulus functoriality]
\label{thm:completion-modulus-category-modulus-functoriality}
Every completion-facing consumer of an accepted $\CompletionModulusCategoryUp$ packet reads a modulus-preserving morphism through the finite route
$$
O,A,S,R,D,F,E,H,C,P,N .
$$
Thus identity and composition of completion morphisms preserve the displayed modulus data before any $\RealUp$ seal or completion-functor read is exposed. The route factors through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CompletionFunctorUp$, and $\CauchyCompletionFunctorUp$ rather than through quotient completion equality, selected representatives, host continuous maps, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Start with a completion-facing morphism request. The object ledger $O$ fixes the source and target completion rows, and the arrow ledger $A$ fixes the modulus transformation to be checked.

The readback rows $S,R,D$ display the inspected stream windows, regular rational observations, and dyadic tolerance comparisons. These rows are the only route by which the requested modulus can face the terminal Real seal.

The functoriality row $F$ then supplies the identity or composition clause. In the identity case the same displayed modulus is replayed. In the composition case the two displayed modulus transformations are composed as finite rows before the result is handed to $E$.

The structural rows $H,C,P,N$ preserve and name the same route. Therefore every completion-functor consumer receives finite modulus preservation data and no excluded quotient, selection, host-map, choice, or ambient-completeness surface.
\end{proof}

\closureat{CompletionModulusCategoryUp}{seedStr}

\begin{closurestatus}{\CompletionModulusCategoryUp}
  \constructivestory{A $\CompletionModulusCategoryUp$ packet is generated from completion object rows, modulus-preserving arrow rows, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance data, RealUp seals, identity and composition rows, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:completion-modulus-category-carrier}, \autoref{thm:completion-modulus-category-namecert-obligations}, and \autoref{thm:completion-modulus-category-modulus-functoriality} seed the finite category surface for modulus-preserving completion morphisms.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, host continuous maps, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus-preserving arrow exactness, identity and composition rows, tolerance readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CompletionModulusCategoryUp.}
\end{closurestatus}
