\chapter{A Concrete Naming Certificate for $\SchwartzKernelUp$}
\label{ch:concrete-instances-schwartz-kernel-namecert}
\origin{human}

Following Schwartz and Gelfand--Shilov, the $\SchwartzKernelUp$ packet records the finite NameCert route by which a distribution kernel is read as a bilinear action between Schwartz test probes and tempered-distribution endpoints. It sits over the Schwartz-function carrier of \autoref{ch:concrete-instances-schwartz-function-namecert}, the tempered-distribution endpoint of \autoref{ch:concrete-instances-tempered-distribution-namecert}, the nuclear factorization row of \autoref{ch:concrete-instances-nuclear-namecert}, the projective tensor norm route of \autoref{ch:concrete-instances-projective-tensor-norm-namecert}, the tensor-product source of \autoref{ch:concrete-instances-tensorproduct-namecert}, and the real seal of \autoref{ch:concrete-instances-real-namecert}. The chapter exposes the kernel theorem as finite action, tensor, nuclearity, bound, transport, replay, provenance, and local naming rows; it does not import a host distribution space, quotient test-function equality, selected representatives, or an unrestricted topological-vector-space oracle.

\begin{definition}[Schwartz kernel carrier]
\label{def:schwartz-kernel-carrier}
A $\SchwartzKernelUp$ carrier is a finite $\BHist$ packet
$$
K=(S,T,U,J,B,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SchwartzFunctionUp$ test-probe row naming the finite seminorm windows inspected on the source side.
\item $T$ is the $\TemperedDistributionUp$ endpoint row naming the distributional action read after the test windows are displayed.
\item $U$ is the $\TensorProductUp$ row naming the finite tensor source on which the two test-probe sides are paired.
\item $J$ is the $\ProjectiveTensorNormUp$ row recording the projective-tensor bound used to compare the paired test windows.
\item $B$ is the $\NuclearUp$ factorization row, exposing the finite nuclear decomposition route by which the kernel action is read.
\item $R$ is the $\RealUp$ seal row for the displayed scalar bounds and kernel-action readbacks.
\item $H$ records componentwise $\hsame$ transport for test probes, tempered endpoint, tensor source, projective bound, nuclear factorization, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite kernel request through $S,T,U,J,B,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\SchwartzKernelUp$, $\SchwartzFunctionUp$, $\TemperedDistributionUp$, $\NuclearUp$, $\ProjectiveTensorNormUp$, $\TensorProductUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SchwartzKernelUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $S,T,U,J,B,R,H,C,P,N$. It has no coordinate for a host distribution space, quotient equality of test functions, selected representatives, ambient bornological completeness, or a topological-vector-space theorem outside the displayed rows.
\end{definition}

\begin{theorem}[Schwartz kernel NameCert obligations]
\label{thm:schwartz-kernel-namecert-obligations}
For every accepted $\SchwartzKernelUp$ carrier
$$
K=(S,T,U,J,B,R,H,C,P,N),
$$
the local $\NameCert_{\SchwartzKernelUp}$ surface consists exactly of Schwartz test-probe admission through $S$, tempered-distribution endpoint admission through $T$, tensor-source admission through $U$, projective-bound exposure through $J$, nuclear-factorization exposure through $B$, scalar RealUp sealing through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.

Every kernel consumer must read the distributional action through these ten rows. No consumer may replace them by an ambient kernel theorem, quotient test-function equality, selected representative, hidden topological vector space, or host nuclear-space completion.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:schwartz-kernel-carrier}. The analytic rows are the Schwartz test row $S$, the tempered-distribution endpoint $T$, the tensor source $U$, the projective bound $J$, the nuclear factorization $B$, and the RealUp seal $R$.

The action route is finite. The tensor row $U$ supplies the paired test-probe source, $J$ records the displayed projective bound, and $B$ records the nuclear factorization by which the kernel action becomes readable by a finite consumer.

Transport and replay do not create new analytic structure. The rows $H$ and $C$ preserve the displayed packet componentwise and replay only the same kernel request. The provenance and naming rows $P,N$ package the route without adding host quotient equality or a hidden completion theorem.

Thus the listed rows are exactly the local NameCert obligations for $\SchwartzKernelUp$.
\end{proof}

\begin{theorem}[Schwartz kernel nuclear factorization boundary]
\label{thm:schwartz-kernel-nuclear-factorization-boundary}
Every accepted $\SchwartzKernelUp$ read factors through the finite route
$$
\SchwartzFunctionUp,\ \TensorProductUp,\ \ProjectiveTensorNormUp,\ \NuclearUp
\longmapsto
\TemperedDistributionUp
\longmapsto
\RealUp .
$$
The nuclear row may expose only the displayed factorization and bound data already routed through $S,U,J$. It exports no host theorem identifying all kernels with all continuous bilinear forms, no quotient equality of test probes, no selected representative of a distribution, and no ambient completeness claim for the surrounding function spaces.
\end{theorem}
\begin{proof}
Start with a kernel read. The request first displays the finite Schwartz windows in $S$ and the tensor source $U$ on which the two test-probe sides are paired.

The projective tensor bound $J$ is the only bound row available to the consumer. The nuclear factorization row $B$ can cite only this displayed tensor-bound route, so its readback is a finite factorization certificate rather than an ambient nuclear-space theorem.

The tempered-distribution endpoint $T$ then reads the resulting action, and $R$ seals the scalar outputs as RealUp data. Transport through $H$ and replay through $C$ keep the same row order, while $P$ and $N$ record source and local naming.

Since no carrier coordinate stores host quotient equality, selected representatives, or ambient completeness, those principles cannot be exported by the factorization boundary.
\end{proof}

\falsifiablePrediction{Every accepted $\SchwartzKernelUp$ packet must expose SchwartzFunctionUp test probes, TensorProductUp source data, ProjectiveTensorNormUp bounds, NuclearUp factorization, TemperedDistributionUp endpoint action, RealUp scalar sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows before a kernel consumer can read the action.}

\independenceWitness{schwartz-function, tempered-distribution, nuclear, projective-tensor-norm, tensorproduct, real: $\SchwartzKernelUp$ is not bijective to any listed sibling because it binds the test-probe tensor route, nuclear factorization boundary, distribution endpoint, and scalar seal as one finite kernel-action packet.}

\closureat{SchwartzKernelUp}{seedStr}

\begin{closurestatus}{\SchwartzKernelUp}
  \constructivestory{A $\SchwartzKernelUp$ packet is generated from SchwartzFunctionUp test probes, a TemperedDistributionUp endpoint, TensorProductUp source data, ProjectiveTensorNormUp bounds, NuclearUp factorization, RealUp scalar seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:schwartz-kernel-carrier}, \autoref{thm:schwartz-kernel-namecert-obligations}, \autoref{thm:schwartz-kernel-nuclear-factorization-boundary}, the falsifiable prediction, and the independence witness seed the finite kernel-action route over Schwartz, tempered-distribution, tensor, nuclear, bound, RealUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host distribution-space semantics, quotient equality of test functions, selected distribution representatives, ambient nuclear-space completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, test-probe visibility, tensor-source admission, projective-bound exactness, nuclear-factorization exposure, tempered-endpoint action, RealUp scalar sealing, componentwise transport and replay stability, provenance exhaustion, and local naming for BEDC.Derived.SchwartzKernelUp.}
\end{closurestatus}
