\chapter{A Concrete Naming Certificate for $\LocallyConnectedUp$}
\label{ch:concrete-instances-locally-connected-namecert}
\origin{human}

Following Kelley and Bourbaki on local connectedness, the $\LocallyConnectedUp$ packet records finite neighbourhood-component data rather than a selected basis of connected open sets. It sits beside the global connectedness carrier of \autoref{ch:concrete-instances-connected-space-namecert}, the compact metric source discipline of \autoref{ch:concrete-instances-compactmetric-namecert}, the metric ball rows of \autoref{ch:concrete-instances-metric-namecert}, and the open-neighbourhood ledger of \autoref{ch:concrete-instances-topology-namecert}. The packet exposes the local component route needed by compact-metric and connected-space consumers without importing path selection, arc connectedness, open-cover compactness, or a host topological basis.

\begin{definition}[Locally connected carrier]
\label{def:locally-connected-carrier}
A $\LocallyConnectedUp$ carrier is a finite $\BHist$ packet
$$
L=(T,M,G,K,B,C,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\TopologyUp$ open-neighbourhood row whose entries name the ambient open requests.
\item $M$ is the $\MetricUp$ ball-observation row used when the local request is metric.
\item $G$ is the $\ConnectedSpaceUp$ global component row available to consumers that compare local and global connectedness.
\item $K$ is the $\CompactMetricUp$ finite-source row available to compact-metric consumers.
\item $B$ is the finite neighbourhood-refinement row: each displayed point and open request has a named smaller neighbourhood row.
\item $C$ is the local connected-component row attached to the refinement in $B$.
\item $H$ records componentwise $\hsame$ transport for the topology, metric, connectedness, compact-metric, refinement, component, provenance, and local naming rows.
\item $R$ records displayed $\Cont$ replay from an ambient open request through metric ball observations when present, the finite refinement row, and the local component row.
\item $P$ is the $\Pkg$ provenance over $\LocallyConnectedUp$, $\TopologyUp$, $\MetricUp$, $\ConnectedSpaceUp$, $\CompactMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocallyConnectedUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,M,G,K,B,C,H,R,P,N$. It has no coordinate for selected paths, arcs, arbitrary open-cover compactness, quotient component spaces, or a host basis of connected neighbourhoods.
\end{definition}

\begin{theorem}[Locally connected NameCert obligations]
\label{thm:locally-connected-namecert-obligations}
For every accepted $\LocallyConnectedUp$ carrier $L=(T,M,G,K,B,C,H,R,P,N)$, the local $\NameCert_{\LocallyConnectedUp}$ surface consists exactly of carrier admission for the topology, metric, connected-space, compact-metric, finite neighbourhood-refinement, local component, transport, replay, provenance, and naming rows; neighbourhood refinement from $T$ through $B$; component exposure through $C$; metric compatibility through $M$ when the request is ball-based; compact-metric compatibility through $K$ for compact finite-source consumers; connected-space comparison through $G$; and non-escape from selected paths, arcs, arbitrary open-cover compactness, quotient component spaces, and host basis choice.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:locally-connected-carrier}. The projection exposes exactly the rows $T,M,G,K,B,C,H,R,P,N$, so every local naming obligation must be read from those coordinates.

The neighbourhood part is finite. An ambient open request is first read in $T$, then refined by the displayed row $B$, and only then receives the local component row $C$.

The metric and compact-metric rows are compatibility rows rather than extra selectors. A ball-based request may inspect $M$, and a compact-metric consumer may inspect $K$, but both routes still pass through the same $B$ and $C$ rows before local connectedness is exported.

Finally, $H$ and $R$ transport and replay the displayed route, while $P$ and $N$ source and name it. Since paths, arcs, arbitrary open-cover compactness, quotient component spaces, and host basis choice are not rows of the carrier, the NameCert surface cannot export them.
\end{proof}

\begin{theorem}[Locally connected neighbourhood component route]
\label{thm:locally-connected-neighborhood-component-route}
Every connected-space or compact-metric consumer of an accepted $\LocallyConnectedUp$ packet reaches local connectedness through
$$
\TopologyUp,\quad \MetricUp,\quad \ConnectedSpaceUp,\quad \CompactMetricUp,\quad \BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
The finite route reads an ambient neighbourhood, optionally reads metric ball observations, refines to a displayed smaller neighbourhood, and then reads the named local connected component. It does not select a path, an arc, a subcover, a quotient component representative, or a host connected-neighbourhood basis.
\end{theorem}
\begin{proof}
Start with a consumer that asks for local connectedness around a displayed point. Carrier admission gives the consumer the topology row $T$, the metric row $M$ when a ball observation is part of the request, the global connectedness row $G$, and the compact-metric row $K$.

The route then passes through $B$ and $C$. The row $B$ supplies the finite neighbourhood refinement, and $C$ supplies the local component attached to that refinement.

The structural rows $H,R,P,N$ do not add a hidden selector. They transport, replay, source, and name the same finite route, so no path, arc, arbitrary subcover, quotient representative, or host basis can replace the displayed neighbourhood-component data.
\end{proof}

\begin{theorem}[Locally connected obligation closure surface]
\label{thm:locally-connected-obligation-closure-surface}
For every accepted $\LocallyConnectedUp$ carrier $L=(T,M,G,K,B,C,H,R,P,N)$, the obligation-closure surface is exhausted by the displayed finite topology, metric, connected-space, compact-metric, neighbourhood-refinement, local-component, transport, replay, provenance, and naming rows. The row $T$ supplies the open-neighbourhood source, $M$ supplies metric-ball observations, $G$ supplies connected-space comparison, $K$ supplies compact-metric finite-source compatibility, $B,C$ supply the local refinement and component rows, and $H,R,P,N$ supply transport, replay, provenance, and local naming.

The local component route therefore consumes the connected-space carrier of \autoref{ch:concrete-instances-connected-space-namecert}, the compact-metric finite neighbourhood discipline of \autoref{ch:concrete-instances-compactmetric-namecert}, the metric-ball rows of \autoref{ch:concrete-instances-metric-namecert}, and the topology neighbourhood ledger of \autoref{ch:concrete-instances-topology-namecert} before a local component can be named.
\end{theorem}
\begin{proof}
Apply \autoref{thm:locally-connected-namecert-obligations} to the accepted carrier. It identifies the complete NameCert surface with the rows $T,M,G,K,B,C,H,R,P,N$.

Apply \autoref{thm:locally-connected-neighborhood-component-route}. The route from an open request to a local component passes through topology, optional metric-ball observations, connected-space comparison, compact-metric compatibility, finite refinement, and component rows before the structural rows transport and name the result.

The sibling lattice is read in that order: topology supplies the neighbourhood ledger, metric supplies ball observations, connected-space supplies the comparison carrier, and compact metric supplies the finite neighbourhood discipline. The local refinement and component rows then bind those sibling contributions into the $\LocallyConnectedUp$ packet.

Thus the obligation surface is the stated finite route. Path or arc selection, open-cover compactness, quotient components, and a host basis are refused because none of them is a carrier coordinate or a row used by the two preceding theorems.
\end{proof}

\falsifiablePrediction{Every accepted $\LocallyConnectedUp$ read must expose a $\TopologyUp$ open-neighbourhood row, optional $\MetricUp$ ball observations, the $\ConnectedSpaceUp$ comparison row when a global consumer is present, the $\CompactMetricUp$ finite-source row when a compact-metric consumer is present, a finite neighbourhood-refinement row, a local component row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{topology, metric, connected-space, compactmetric: $\LocallyConnectedUp$ is not bijective to any listed sibling because it binds a local neighbourhood-refinement row to a local component row before connected-space or compact-metric consumers may read the result.}

\closureat{LocallyConnectedUp}{seedStr}

\begin{closurestatus}{\LocallyConnectedUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:locally-connected-carrier}, \autoref{thm:locally-connected-namecert-obligations}, and \autoref{thm:locally-connected-neighborhood-component-route} seed the finite local neighbourhood-component route over topology, metric, connected-space, and compact-metric rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close path connectedness, arc connectedness, arbitrary open-cover compactness, quotient component spaces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, neighbourhood refinement, local component exposure, connected-space comparison, compact-metric compatibility, transport and replay stability, provenance exhaustion, and TasteGate field faithfulness for BEDC.Derived.LocallyConnectedUp.}
  \constructivestory{A $\LocallyConnectedUp$ packet is generated from an open-neighbourhood row, optional metric ball observations, connected-space and compact-metric compatibility rows, a finite neighbourhood-refinement row, a local component row, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
\end{closurestatus}
