\chapter{A Concrete Naming Certificate for $\SynonymousTransitionUp$}
\label{ch:concrete-instances-synonymous-transition-namecert}
\origin{ai}

The $\SynonymousTransitionUp$ packet realizes the finite synonymous-transition geometry of \autoref{thm:philosophy-largest-class-adjacency-weights} as BEDC NameCert data. It sits beside the six-bit codon-window carrier of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the codon transition matrix of \autoref{ch:concrete-instances-codon-transition-matrix-namecert}, the DNA boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the window-coverage trigger algebra of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}, and the DNA-window trigger threshold of \autoref{ch:concrete-instances-dna-window-six-trigger-threshold-namecert}. The packet names finite codon-window, class-adjacency, boundary-spectrum, threshold, transport, replay, provenance, and local naming rows; it is not a biological mechanism, stochastic fitness model, quotient codon semantics, or unrecorded enumeration oracle.

\begin{definition}[Synonymous transition carrier]
\label{def:synonymous-transition-carrier}
A $\SynonymousTransitionUp$ carrier is a finite $\BHist$ packet
$$
G=(W,M,A,B,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ row naming the finite $Q_{6}$ codon-window surface.
\item $M$ is the $\CodonTransitionMatrixUp$ row naming one-bit codon transitions inspected by the packet.
\item $A$ is the class-adjacency row recording the displayed synonymous and cross-class adjacency counts, including the largest weights of \autoref{thm:philosophy-largest-class-adjacency-weights}.
\item $B$ is the boundary-spectrum row recording internal edge counts, external boundary degrees, and the control-pair corner-contact data.
\item $T$ is the $\DNAWindowSixTriggerThresholdUp$ row naming the finite threshold at which an adjacency or boundary-spectrum read may trigger a downstream tile consumer.
\item $H$ records componentwise $\hsame$ transport for codon windows, transition matrix, class adjacency, boundary spectrum, trigger threshold, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite synonymous-transition request through $W,M,A,B,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\SynonymousTransitionUp$, $\CodonSixBitWindowUp$, $\CodonTransitionMatrixUp$, $\DnaWindowSixBoundaryTileUp$, $\WindowCoverageTriggerAlgebraUp$, $\DNAWindowSixTriggerThresholdUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SynonymousTransitionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $W,M,A,B,T,H,C,P,N$. It has no coordinate for biological mechanism, stochastic fitness, quotient codon equality, hidden enumeration, or an ambient graph-theory oracle outside the displayed finite rows.
\end{definition}

\begin{theorem}[Synonymous transition NameCert obligations]
\label{thm:synonymous-transition-namecert-obligations}
For every accepted $\SynonymousTransitionUp$ carrier
$$
G=(W,M,A,B,T,H,C,P,N),
$$
the local $\NameCert_{\SynonymousTransitionUp}$ surface consists exactly of codon-window admission through $W$, transition-matrix admission through $M$, class-adjacency exposure through $A$, boundary-spectrum exposure through $B$, trigger-threshold exposure through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.

Every downstream synonymous-transition consumer must read the graph through these nine rows. It cannot replace them by biological causation, stochastic selection, quotient codon semantics, an unrecorded enumeration, or a hidden graph oracle.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:synonymous-transition-carrier}. The finite codon surface is $W$, the one-bit transition source is $M$, and the named graph data are the class-adjacency row $A$ and boundary-spectrum row $B$.

The trigger row $T$ records when the displayed adjacency or boundary-spectrum data may be read by a downstream tile or trigger consumer. It does not add a biological mechanism or a stochastic model; it only names the finite threshold over the same graph rows.

Transport and replay are componentwise. The rows $H$ and $C$ preserve and replay $W,M,A,B,T$ with the same finite endpoints, while $P$ and $N$ record provenance and local naming.

Since the carrier has no coordinate for quotient codon equality, hidden enumeration, biological causation, or ambient graph semantics, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Synonymous transition boundary-spectrum handoff]
\label{thm:synonymous-transition-boundary-spectrum-handoff}
Every accepted $\SynonymousTransitionUp$ read factors through the finite route
$$
\CodonSixBitWindowUp,\ \CodonTransitionMatrixUp
\longmapsto
\SynonymousTransitionUp
\longmapsto
\DnaWindowSixBoundaryTileUp,\ \WindowCoverageTriggerAlgebraUp,\ \DNAWindowSixTriggerThresholdUp .
$$
The handoff exposes class-adjacency weights, internal-edge counts, external boundary degrees, and control-pair corner contacts only as finite packet rows. It exports no biological mechanism, stochastic fitness model, quotient codon semantics, or unrecorded enumeration oracle.
\end{theorem}
\begin{proof}
Start with the codon-window row $W$ and the one-bit transition matrix row $M$. These rows supply the finite $Q_{6}$ source and the adjacency relation inspected by the packet.

The class-adjacency row $A$ records the largest displayed weights, and $B$ records the boundary-spectrum data. The downstream boundary-tile and trigger-algebra consumers therefore receive a finite graph packet rather than a biological or stochastic explanation.

The threshold row $T$ names when the finite rows can be consumed by the trigger route. Transport through $H$ and replay through $C$ keep the same graph rows visible, while $P$ and $N$ only package their provenance and local name.

Thus every public read of the synonymous-transition geometry remains inside the finite codon-window, transition, adjacency, boundary-spectrum, threshold, transport, replay, provenance, and naming surface.
\end{proof}

\falsifiablePrediction{Every accepted $\SynonymousTransitionUp$ packet must expose CodonSixBitWindowUp, CodonTransitionMatrixUp, class-adjacency, boundary-spectrum, DNAWindowSixTriggerThresholdUp, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows before a downstream tile or trigger consumer can read the synonymous-transition graph.}

\independenceWitness{codon-six-bit-window, codon-transition-matrix, dna-window-six-boundary-tile, window-coverage-trigger-algebra, dna-window-six-trigger-threshold: $\SynonymousTransitionUp$ is not bijective to any listed sibling because it jointly carries class-adjacency weights, boundary-spectrum rows, and trigger-threshold handoff over the finite codon-window graph.}

\closureat{SynonymousTransitionUp}{seedStr}

\begin{closurestatus}{\SynonymousTransitionUp}
  \constructivestory{A $\SynonymousTransitionUp$ packet is generated from a CodonSixBitWindowUp source, a CodonTransitionMatrixUp one-bit transition row, class-adjacency counts, boundary-spectrum data, DNAWindowSixTriggerThresholdUp rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:synonymous-transition-carrier}, \autoref{thm:synonymous-transition-namecert-obligations}, \autoref{thm:synonymous-transition-boundary-spectrum-handoff}, the falsifiable prediction, and the independence witness seed the finite synonymous-transition packet over codon-window, transition, adjacency, boundary-spectrum, threshold, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological mechanism, stochastic fitness, quotient codon semantics, hidden enumeration, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, codon-window visibility, transition-matrix exactness, class-adjacency exposure, boundary-spectrum exposure, trigger-threshold handoff, componentwise transport and replay stability, provenance exhaustion, and local naming for BEDC.Derived.SynonymousTransitionUp.}
\end{closurestatus}
