\chapter{A Concrete Naming Certificate for $\MetaCICNormalEndpointBudgetUp$}
\label{ch:concrete-instances-metacic-normal-endpoint-budget-namecert}
\origin{ai}

The $\MetaCICNormalEndpointBudgetUp$ packet realizes the normal-endpoint budget from the MetaCIC normalization frontier as finite NameCert data. It sits beside \autoref{ch:concrete-instances-metacic-strong-normalization-boundary-namecert}, \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}, \autoref{ch:concrete-instances-metacicconfluencenormalfragment-namecert}, \autoref{ch:concrete-instances-znormal-namecert}, and \autoref{ch:concrete-instances-bounded-normal-conversion-bridge-namecert}. The packet names the accepted endpoint budget that consistency consumers may inspect; it does not erase the obstruction against blanket strong normalization.

\begin{definition}[MetaCIC normal-endpoint budget carrier]
\label{def:metacic-normal-endpoint-budget-carrier}
A $\MetaCICNormalEndpointBudgetUp$ carrier is a finite $\BHist$ packet
$$
E=(T,K,B,F,O,H,C,P,N,G)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the typed closed-term or typed fragment row whose normal endpoint is being budgeted.
\item $K$ is the candidate-evidence row, read before any normalization-facing consumer sees an endpoint.
\item $B$ is the bounded-normal endpoint row, recording the finite fuel, reduction trace, and bounded checker evidence available for $T$.
\item $F$ is the finished-normal seal row, exposing the normal endpoint only after candidate evidence and bounded computation rows have been displayed.
\item $O$ is the obstruction row, recording the retained subject-reduction or confluence boundary when the endpoint budget is unavailable for a wider theorem.
\item $H$ records componentwise $\hsame$ transport for typed rows, candidate evidence, bounded endpoints, finished-normal seals, obstruction rows, replay, provenance, local naming, and gate rows.
\item $C$ records displayed $\Cont$ replay from endpoint requests through $T,K,B,F,O$.
\item $P$ is the $\Pkg$ provenance over $\MetaCICNormalEndpointBudgetUp$, the MetaCIC strong-normalization boundary, the subject-reduction obstruction, the confluence-normal fragment, $\ZNormalUp$, the bounded-normal conversion bridge, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetaCICNormalEndpointBudgetUp}$ row.
\item $G$ is the TasteGate landing row requiring $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for the displayed carrier surface before the packet is treated as a closed audit object.
\end{enumerate}
The classifier compares accepted packets only through $T,K,B,F,O,H,C,P,N,G$. It has no coordinate for evidence-free strong normalization, unrestricted subject reduction, quotient conversion equality, hidden fuel, or an unbounded normalizer.
\end{definition}

\begin{theorem}[MetaCIC normal-endpoint budget NameCert obligations]
\label{thm:metacic-normal-endpoint-budget-namecert-obligations}
For every accepted $\MetaCICNormalEndpointBudgetUp$ carrier $E=(T,K,B,F,O,H,C,P,N,G)$, the local $\NameCert_{\MetaCICNormalEndpointBudgetUp}$ surface consists exactly of candidate evidence, bounded-normal endpoint, finished-normal seal, obstruction retention, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, local naming, and TasteGate landing obligations. Every consistency-facing consumer must display those rows before it reads the endpoint budget.
\end{theorem}
\begin{proof}
Project the accepted carrier. The typed row $T$ is only a source row; it is not a normalization theorem by itself.

The candidate row $K$ is read before the bounded endpoint row $B$. The finished-normal seal $F$ is downstream of both rows, so a consumer cannot reach the normal endpoint without candidate evidence and bounded computation evidence.

The obstruction row $O$ remains part of the same packet. It records the subject-reduction or confluence boundary that blocks reading the endpoint budget as a blanket strong-normalization theorem.

Finally $H,C,P,N,G$ transport, replay, source, name, and gate the same carrier. Since the classifier has no hidden fuel coordinate, unbounded normalizer, quotient conversion equality, or evidence-free theorem row, the listed obligations exhaust the endpoint budget surface.
\end{proof}

\begin{theorem}[MetaCIC normal-endpoint budget consistency boundary]
\label{thm:metacic-normal-endpoint-budget-consistency-boundary}
Every consistency-facing read from an accepted $\MetaCICNormalEndpointBudgetUp$ packet factors through the finite route from \autoref{ch:concrete-instances-metacic-strong-normalization-boundary-namecert} through \autoref{ch:concrete-instances-metacic-subject-reduction-obstruction-namecert}, \autoref{ch:concrete-instances-metacicconfluencenormalfragment-namecert}, \autoref{ch:concrete-instances-znormal-namecert}, and \autoref{ch:concrete-instances-bounded-normal-conversion-bridge-namecert}, as mediated by the rows $T,K,B,F,O,H,C,P,N,G$. Thus the endpoint can support a bounded normal-consistency read only while candidate evidence, obstruction retention, and finished-normal sealing remain displayed.
\end{theorem}
\begin{proof}
Use the obligation theorem to expose the row order. Candidate evidence $K$ and bounded endpoint evidence $B$ precede the finished-normal seal $F$.

The obstruction row $O$ remains visible between the strong-normalization boundary and the subject-reduction or confluence frontier. Therefore the route through the confluence-normal fragment, $\ZNormalUp$ endpoint, and bounded-normal conversion bridge is a finite endpoint budget, not a full subject-reduction or strong-normalization theorem.

Transport, replay, provenance, local naming, and the TasteGate landing row preserve the same dependency order. A consistency consumer therefore reads the normal endpoint only as a displayed budget with retained obstruction evidence.
\end{proof}

\falsifiablePrediction{Every accepted $\MetaCICNormalEndpointBudgetUp$ packet must display candidate evidence, bounded-normal endpoint, finished-normal seal, obstruction, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows before any consistency consumer reads it.}

\independenceWitness{metacic-strong-normalization-boundary, metacic-subject-reduction-obstruction, metacicconfluencenormalfragment, znormal, bounded-normal-conversion-bridge: the normal-endpoint budget consumes those sibling frontiers as independent rows and does not collapse them into a blanket strong-normalization or subject-reduction theorem.}

The Lean TasteGate landing condition for $\MetaCICNormalEndpointBudgetUp$ includes explicit $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for the displayed carrier surface.

\closureat{MetaCICNormalEndpointBudgetUp}{seedStr}

\begin{closurestatus}{\MetaCICNormalEndpointBudgetUp}
  \constructivestory{A $\MetaCICNormalEndpointBudgetUp$ packet is generated from typed MetaCIC source rows, candidate evidence, bounded-normal endpoint evidence, a finished-normal seal, obstruction retention, componentwise hsame transport, displayed Cont replay, Pkg provenance, local NameCert data, and TasteGate landing rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-normal-endpoint-budget-carrier}, \autoref{thm:metacic-normal-endpoint-budget-namecert-obligations}, and \autoref{thm:metacic-normal-endpoint-budget-consistency-boundary} seed the finite normal-endpoint budget for consistency-facing MetaCIC consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, blanket strong normalization, unrestricted subject reduction, quotient conversion equality, hidden fuel, or an unbounded normalizer.}
  \upgradepath{Obligation closure requires checked candidate evidence, bounded-normal endpoint, finished-normal seal, obstruction retention, transport, replay, provenance, local naming, and TasteGate Nontrivial and FieldFaithful rows for BEDC.Derived.MetaCICNormalEndpointBudgetUp.}
\end{closurestatus}
