\chapter{A Concrete Naming Certificate for $\PrivateCoordinateTriggerUp$}
\label{ch:concrete-instances-private-coordinate-trigger-namecert}
\origin{ai}

The $\PrivateCoordinateTriggerUp$ packet realizes the private-coordinate minimal-cover theorem of \autoref{thm:philosophy-private-coordinate-trigger-enumeration-theorem} as finite NameCert data. It records a trigger-coordinate carrier, a support-family cover ledger, and one private-coordinate witness row for each displayed support before any minimal-trigger criterion may be consumed. The packet keeps the enumeration theorem auditable without identifying it with a generic finite set, word list, Boolean classifier, regular-language recognizer, or finite automaton presentation.

\falsifiablePrediction{Every accepted $\PrivateCoordinateTriggerUp$ consumer must display a cover row and one private-coordinate witness row for each support before using the minimal-trigger criterion.}

\independenceWitness{finset, list, bool, regularlanguage, finite-automaton: $\PrivateCoordinateTriggerUp$ is not bijective to these siblings because it carries a support-family cover ledger plus a private-coordinate witness for every support row.}

\begin{definition}[Private-coordinate trigger carrier]
\label{def:private-coordinate-trigger-carrier}
A $\PrivateCoordinateTriggerUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
T=(\Omega,A,U,V,\pi,E,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $\Omega$ is the finite trigger-coordinate row.
\item $A$ is the finite support-family row whose entries are displayed subsets of $\Omega$.
\item $U$ is the cover ledger asserting that the displayed supports cover every coordinate of $\Omega$.
\item $V$ is the private-coordinate witness ledger, with one row for each support in $A$.
\item $\pi$ maps each support row to its selected private coordinate and records membership in that support.
\item $E$ records exclusion from every other support row for the selected private coordinate.
\item $K$ is the minimal-cover criterion row, readable only after $U,V,\pi,E$ have been displayed.
\item $H$ stores componentwise $\hsame$ transport for coordinate, support, cover, witness, exclusion, and criterion rows.
\item $C$ stores $\Cont$ replay from a trigger query through the cover ledger and the private-coordinate witness rows.
\item $P$ stores $\Pkg$ provenance over $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PrivateCoordinateTriggerUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $\Omega,A,U,V,\pi,E,K,H,C,P,N$. It has no coordinate for a bare finite set, unordered list, Boolean truth table, regular-language recognizer, finite automaton run, or support family without displayed private witnesses.
\end{definition}

\begin{theorem}[Private-coordinate trigger NameCert obligations]
\label{thm:private-coordinate-trigger-namecert-obligations}
For every accepted $\PrivateCoordinateTriggerUp$ carrier
$$
T=(\Omega,A,U,V,\pi,E,K,H,C,P,N),
$$
the local $\NameCert_{\PrivateCoordinateTriggerUp}$ surface consists exactly of coordinate exposure, support-family exposure, cover-ledger replay, one private-coordinate witness row for each support, membership and exclusion checks for the selected witnesses, minimal-cover criterion exposure, componentwise transport, continuation replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:private-coordinate-trigger-carrier}. The rows $\Omega,A,U$ display the finite coordinate space, the support family, and the fact that the supports cover the full coordinate row.

The rows $V,\pi,E$ attach a private coordinate to each support. Membership is recorded by $\pi$, and exclusion from every other support is recorded by $E$, so deleting the support removes at least one displayed coordinate from the cover.

The criterion row $K$ is therefore readable only after the cover and private-witness rows have been exposed. The remaining rows $H,C,P,N$ preserve transport, replay, provenance, and local naming for the same finite packet, and no omitted sibling surface supplies the private-coordinate ledger.
\end{proof}

\begin{theorem}[Private-coordinate minimal-cover criterion]
\label{thm:private-coordinate-trigger-minimal-cover-criterion}
Every accepted $\PrivateCoordinateTriggerUp$ carrier exposes a minimal full trigger exactly through the displayed cover row $U$ together with the private-coordinate witness rows $V,\pi,E$. A consumer may use the criterion row $K$ only after reading a cover of $\Omega$ and one witness coordinate for every support row in $A$ that belongs to that support and belongs to no other displayed support. The packet does not turn the support family into a regular language, finite automaton, Boolean table, or list quotient.
\end{theorem}
\begin{proof}
The forward read uses the cover ledger $U$ and the private-coordinate witness rows. If a support row is removed, its selected witness coordinate remains outside all other displayed supports by $E$, so the remaining family no longer covers $\Omega$.

For the reverse read, the cover row already gives full coverage. The witness rows ensure that every support has a coordinate lost by deleting that support, so no displayed support is redundant.

Thus the criterion row $K$ is exactly the finite private-coordinate minimal-cover test. The transport, replay, provenance, and local naming rows carry this test without converting it into any sibling classifier.
\end{proof}

\closureat{PrivateCoordinateTriggerUp}{seedStr}

\begin{closurestatus}{\PrivateCoordinateTriggerUp}
  \constructivestory{A $\PrivateCoordinateTriggerUp$ packet is generated from a finite trigger-coordinate row, support-family row, cover ledger, per-support private-coordinate witness ledger, membership and exclusion rows, minimal-cover criterion row, componentwise transport, continuation replay, provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:private-coordinate-trigger-carrier}, \autoref{thm:private-coordinate-trigger-namecert-obligations}, and \autoref{thm:private-coordinate-trigger-minimal-cover-criterion} seed the finite NameCert packet for private-coordinate minimal-cover witnesses.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, regular-language recognition, finite-automaton minimization, Boolean classifier completeness, or enumeration beyond the displayed private-coordinate criterion.}
  \upgradepath{Obligation closure requires checked carrier admission, cover-ledger replay, private-coordinate witness coverage, exclusion exactness, minimal-cover criterion replay, TasteGate nontriviality, FieldFaithful projection, transport, replay, provenance, and local naming for BEDC.Derived.PrivateCoordinateTriggerUp.}
\end{closurestatus}
