\chapter{A Concrete Naming Certificate for $\HyperbolicTranslationLengthUp$}
\label{ch:concrete-instances-hyperbolic-translation-length-namecert}
\origin{human}

Following the classical translation length of a hyperbolic isometry, the $\HyperbolicTranslationLengthUp$ packet records the finite invariant-length route visible to the hyperbolic phase geometry of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion}. It consumes the metric-read surface of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the routed geodesic-flow surface of \autoref{ch:concrete-instances-hyperbolic-geodesic-flow-namecert}, the additive Busemann cocycle route of \autoref{ch:concrete-instances-hyperbolic-busemann-cocycle-namecert}, the four-boundary-point comparison of \autoref{ch:concrete-instances-hyperbolic-cross-ratio-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet names stable displacement growth as finite BEDC data; it does not import a host hyperbolic manifold, quotient ideal boundary, selected axis, spectral radius, or global curvature theorem.

\begin{definition}[HyperbolicTranslationLength carrier]
\label{def:hyperbolic-translation-length-carrier}
A $\HyperbolicTranslationLengthUp$ carrier is a finite $\BHist$ packet
$$
L=(M,F,B,X,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\HyperbolicMetricUp$ row, exposing displacement reads for the source and its iterated image.
\item $F$ is the $\HyperbolicGeodesicFlowUp$ row, recording the finite routed-flow data used to compare iterates along the same visible geodesic route.
\item $B$ is the $\HyperbolicBusemannCocycleUp$ row, supplying additive boundary-cocycle comparisons for the same displayed endpoints.
\item $X$ is the $\HyperbolicCrossRatioUp$ row, recording the four-boundary-point invariant used to stabilize the length read.
\item $R$ is the $\RealUp$ row used by displacement values, additive cocycle values, cross-ratio reads, and the final nonnegative length seal.
\item $D$ is the displacement-growth row, comparing the displayed iterate window through $M,F,B,X,R$ without selecting an infinite orbit or an axis.
\item $E$ is the endpoint-stability row, stating that the same boundary data are replayed by the metric, flow, Busemann, and cross-ratio rows.
\item $H$ records componentwise $\hsame$ transport for $M,F,B,X,R,D,E$ and for the local structural rows.
\item $C$ records displayed $\Cont$ replay from a translation-length request through $M,F,B,X,R,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicTranslationLengthUp$, $\HyperbolicMetricUp$, $\HyperbolicGeodesicFlowUp$, $\HyperbolicBusemannCocycleUp$, $\HyperbolicCrossRatioUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicTranslationLengthUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host isometry group, selected invariant axis, quotient boundary equality, spectral radius, completed hyperbolic manifold, or physical expansion law.
\end{definition}

\begin{theorem}[HyperbolicTranslationLength NameCert obligations]
\label{thm:hyperbolic-translation-length-namecert-obligations}
For every accepted $\HyperbolicTranslationLengthUp$ carrier $L=(M,F,B,X,R,D,E,H,C,P,N)$, the local $\NameCert_{\HyperbolicTranslationLengthUp}$ surface consists exactly of metric displacement visibility, geodesic-flow routing, Busemann additivity, cross-ratio stabilization, real-valued length sealing, displacement-growth comparison, endpoint stability, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No obligation is stored outside $M,F,B,X,R,D,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-translation-length-carrier}. The rows $M,F,B,X,R,D,E,H,C,P,N$ are the whole visible packet.

The geometric route is read first. Metric displacement comes from $M$, routed iteration from $F$, additive boundary comparison from $B$, and four-boundary-point stabilization from $X$.

The Real and displacement rows then seal the length read. The row $R$ supplies the real-valued comparison surface, while $D$ and $E$ ensure that the same endpoint data are used by the metric, flow, Busemann, and cross-ratio reads.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no carrier coordinate names a host isometry group, selected invariant axis, quotient boundary equality, spectral radius, completed manifold, or physical expansion law, the listed obligations exhaust the local surface.
\end{proof}

\begin{theorem}[HyperbolicTranslationLength invariant route]
\label{thm:hyperbolic-translation-length-invariant-route}
Every accepted $\HyperbolicTranslationLengthUp$ read factors through
$$
\HyperbolicMetricUp,\HyperbolicGeodesicFlowUp,\HyperbolicBusemannCocycleUp,\HyperbolicCrossRatioUp,\RealUp \longmapsto H,C,P,N .
$$
The finite route records displacement growth and boundary stabilization as a real-sealed invariant length, and it exports no host hyperbolic isometry, selected axis, quotient ideal-boundary equality, spectral radius, completed hyperbolic manifold, or cosmological expansion claim.
\end{theorem}
\begin{proof}
Begin with the displacement request. The metric row $M$ supplies finite distance reads, and the geodesic-flow row $F$ keeps the iterated comparison on the same displayed route.

Read boundary stabilization next. The Busemann cocycle row $B$ supplies additive endpoint comparison, while the cross-ratio row $X$ records the four-boundary-point invariant. The endpoint-stability row $E$ requires these boundary reads to describe the same displayed data.

The Real row $R$ and displacement-growth row $D$ seal the invariant length as a finite real-valued read. The structural rows $H,C,P,N$ preserve, replay, source, and name that route, while the excluded host and quotient objects remain absent from the carrier.
\end{proof}

\falsifiablePrediction{An accepted $\HyperbolicTranslationLengthUp$ consumer is refuted if it obtains an invariant length without displaying the $\HyperbolicMetricUp$, $\HyperbolicGeodesicFlowUp$, $\HyperbolicBusemannCocycleUp$, $\HyperbolicCrossRatioUp$, $\RealUp$, displacement-growth, endpoint-stability, transport, replay, provenance, and local $\NameCert$ rows.}

\independenceWitness{hyperbolicmetric, hyperbolic-geodesic-flow, hyperbolic-busemann-cocycle, hyperbolic-cross-ratio, real: no listed sibling is bijective to $\HyperbolicTranslationLengthUp$ because the packet jointly carries metric displacement, routed flow, additive boundary cocycle, cross-ratio stabilization, Real sealing, displacement-growth comparison, endpoint stability, transport, replay, package provenance, and local naming.}

\closureat{HyperbolicTranslationLengthUp}{seedStr}

\begin{closurestatus}{\HyperbolicTranslationLengthUp}
  \constructivestory{A $\HyperbolicTranslationLengthUp$ packet is generated from HyperbolicMetric displacement rows, HyperbolicGeodesicFlow routing rows, HyperbolicBusemannCocycle additive boundary rows, HyperbolicCrossRatio stabilization rows, Real sealing rows, displacement-growth and endpoint-stability rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-translation-length-carrier}, \autoref{thm:hyperbolic-translation-length-namecert-obligations}, and \autoref{thm:hyperbolic-translation-length-invariant-route} seed the finite invariant-length packet over metric, flow, Busemann, cross-ratio, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host hyperbolic isometries, selected axes, quotient ideal-boundary equality, spectral radii, completed hyperbolic manifolds, physical expansion laws, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, displacement visibility, flow routing, Busemann additivity, cross-ratio stabilization, Real length sealing, endpoint stability, and local naming for BEDC.Derived.HyperbolicTranslationLengthUp.}
\end{closurestatus}
