\chapter{A Concrete Naming Certificate for $\FiniteCauchyFilterUp$}
\label{ch:concrete-instances-finite-cauchy-filter-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\FiniteCauchyFilterUp$ packet records the finite directed-tail surface used when a completion consumer asks for Cauchy-filter evidence before reading a regular rational name or a terminal real-name seal. It sits beside the finite stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite filter basis for tail requests; it is not a quotient filter, a selected limit, countable choice, host real equality, or a completeness theorem for $\RealUp$.

\begin{definition}[Finite Cauchy filter carrier]
\label{def:finite-cauchy-filter-carrier}
A $\FiniteCauchyFilterUp$ carrier is a finite $\BHist$ packet
$$
F=(W,T,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\StreamNameUp$ row recording the finite source windows inspected by the filter request.
\item $T$ is the directed-tail request row, naming the finite family of later-window obligations and their refinement order.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the dyadic radii and comparison budgets used by the directed tails.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed windows and tolerance ledger.
\item $E$ is the $\RealUp$ seal row reachable only after $W,T,D,R$ have been exposed.
\item $H$ records componentwise $\hsame$ transport for the stream windows, tail requests, dyadic ledgers, regular readback, and real seal.
\item $C$ records displayed $\Cont$ replay of the same finite filter route.
\item $P$ records $\Pkg$ provenance over $\FiniteCauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FiniteCauchyFilterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,T,D,R,E,H,C,P,N$. It has no coordinate for quotient filters, selected limits, countable choice, host equality of streams, host real equality, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Finite Cauchy filter NameCert obligations]
\label{thm:finite-cauchy-filter-namecert-obligations}
For the carrier of \autoref{def:finite-cauchy-filter-carrier}, the local $\NameCert_{\FiniteCauchyFilterUp}$ surface consists exactly of carrier admission, finite $\StreamNameUp$ window exposure, directed-tail request visibility, $\DyadicRatCoreUp$ tolerance-ledger preservation, $\RegSeqRatUp$ readback, $\RealUp$ seal access, componentwise transport, displayed continuation replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the accepted packet $F=(W,T,D,R,E,H,C,P,N)$. The rows $W,T,D$ expose the finite source windows, directed tail requests, and dyadic tolerance budgets before any regular-rational or real-facing read is admitted.

The readback row $R$ is then determined by the displayed windows and tolerance ledger. Since the carrier stores no second regular-rational coordinate, every $\RegSeqRatUp$ consumer reads the same finite route.

The seal row $E$ is downstream of $W,T,D,R$. The transport row $H$, continuation row $C$, package provenance row $P$, and local naming row $N$ preserve exactly that route and provide no coordinate for quotient filters, selected limits, countable choice, host stream equality, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[Finite Cauchy filter Real route]
\label{thm:finite-cauchy-filter-real-route}
Every $\RealUp$-facing consumer of an accepted $\FiniteCauchyFilterUp$ carrier factors through the finite route
$$
W,T,D,R,E,H,C,P,N .
$$
In particular, the consumer must first read $\StreamNameUp$ windows, directed tail requests, $\DyadicRatCoreUp$ tolerance ledgers, and the $\RegSeqRatUp$ readback before the terminal $\RealUp$ seal is consumed.
\end{theorem}
\begin{proof}
Start with the carrier definition. The only real-facing row is $E$, and it is displayed after the stream windows, directed-tail row, dyadic ledger, and regular readback row.

Apply \autoref{thm:finite-cauchy-filter-namecert-obligations}. The local NameCert surface admits the real seal only as part of the same transport, continuation, provenance, and naming route.

Thus any Real-facing consumer receives the finite packet $W,T,D,R,E,H,C,P,N$ and no quotient-filter, selected-limit, countable-choice, host-equality, or ambient-completeness substitute.
\end{proof}

\closureat{FiniteCauchyFilterUp}{seedStr}

\begin{closurestatus}{\FiniteCauchyFilterUp}
  \constructivestory{A $\FiniteCauchyFilterUp$ packet is generated from finite StreamName windows, directed tail requests, DyadicRatCore tolerance ledgers, RegSeqRat readback, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-cauchy-filter-carrier}, \autoref{thm:finite-cauchy-filter-namecert-obligations}, and \autoref{thm:finite-cauchy-filter-real-route} specify the finite directed-tail filter carrier and its Real-facing route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filter construction, selected limits, countable choice, host stream equality, host real equality, ambient completeness of $\RealUp$, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean carrier encoding and checked theorems for directed-tail visibility, tolerance-ledger preservation, readback, Real seal routing, transport, replay, provenance, and local naming.}
\end{closurestatus}
