\chapter{A Concrete Naming Certificate for $\HausdorffCompletionEnvelopeUp$}
\label{ch:concrete-instances-hausdorff-completion-envelope-namecert}
\origin{human}

Following Bourbaki and Kelley, the $\HausdorffCompletionEnvelopeUp$ packet records the separated completion boundary needed by the L10 Real and Completion route as finite BEDC data. It sits after the separation predicate of \autoref{ch:concrete-instances-hausdorffspace-namecert}, the separated-completion carrier of \autoref{ch:concrete-instances-separatedcompletion-namecert}, the metric completion route of \autoref{ch:concrete-instances-metriccompletion-namecert}, the finite stream interface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the envelope through displayed rows only; it does not quotient filters, select representatives, identify host equalities, invoke countable choice, or import ambient completeness.

\begin{definition}[Hausdorff completion envelope carrier]
\label{def:hausdorff-completion-envelope-carrier}
A $\HausdorffCompletionEnvelopeUp$ carrier is a finite packet
$$
E=(H,S,M,W,D,R,L,T,K,P,N)
$$
where $H$ is the displayed $\HausdorffSpaceUp$ separation row, $S$ is the $\SeparatedCompletionUp$ boundary row, $M$ is the $\MetricCompletionUp$ route row, $W$ is the finite $\StreamNameUp$ observation row, $D$ is the $\DyadicRatCoreUp$ tolerance ledger, $R$ is the $\RegSeqRatUp$ readback row, $L$ is the terminal $\RealUp$ seal, $T$ is componentwise $\BHist/\hsame$ transport, $K$ is displayed $\Cont$ replay, $P$ is $\Pkg$ provenance, and $N$ is the local $\NameCert_{\HausdorffCompletionEnvelopeUp}$ row. A consumer of $E$ receives a separated completion boundary only through these coordinates.
\end{definition}
\leanchecked{BEDC.Derived.HausdorffCompletionEnvelopeUp.HausdorffCompletionEnvelopeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Hausdorff completion envelope obligations]
\label{thm:hausdorff-completion-envelope-obligations}
Every accepted $\NameCert_{\HausdorffCompletionEnvelopeUp}$ read must expose the carrier of \autoref{def:hausdorff-completion-envelope-carrier} in the order
$$
H,S,M,W,D,R,L,T,K,P,N .
$$
The separation row $H$ and separated-completion row $S$ are available before metric completion, stream observation, dyadic tolerance, regular readback, and real-seal rows are consumed; the transport, replay, provenance, and naming rows preserve the same displayed packet.
\end{theorem}
\leanchecked{BEDC.Derived.HausdorffCompletionEnvelopeUp.HausdorffCompletionEnvelopeNameCertObligations}
\begin{proof}
Project the carrier of \autoref{def:hausdorff-completion-envelope-carrier}. The packet has no completion-facing coordinates except $H,S,M,W,D,R,L,T,K,P,N$.

The Hausdorff and separated-completion rows are the first boundary data in the packet. Thus a consumer cannot inspect the metric completion route, finite stream windows, dyadic tolerances, regular readback, or terminal real seal without first reading the displayed separation surface.

Finally, the structural rows $T,K,P,N$ only transport, replay, source, and name the same finite packet. They do not create quotient filters, selected representatives, host equality, choice-selected routes, or ambient completeness.
\end{proof}

\begin{theorem}[Hausdorff completion separated metric route]
\label{thm:hausdorff-completion-envelope-separated-metric-route}
Every $\MetricCompletionUp$ or $\RealUp$ consumer of a $\HausdorffCompletionEnvelopeUp$ carrier factors through the separated route
$$
H,S \longmapsto M \longmapsto W,D,R,L .
$$
The route records a separated metric-completion boundary for the L10 Real and Completion interface, not a quotient completion, a host equality theorem, a choice-selected representative, or an ambient completeness principle.
\end{theorem}
\leanchecked{BEDC.Derived.HausdorffCompletionEnvelopeUp.HausdorffCompletionEnvelopeCarrier\_separated\_metric\_route}
\begin{proof}
Start from \autoref{thm:hausdorff-completion-envelope-obligations}. It places the Hausdorff row $H$ and separated-completion row $S$ before the metric completion row $M$ and before the stream, dyadic, regular-rational, and real-seal rows.

Read the metric completion route through $M$. Since $M$ is downstream of $H,S$, every completion-facing use of $M$ carries the displayed separated boundary with it.

The final Real-facing read is the finite route $W,D,R,L$. Because these rows are still coordinates of the same carrier, the route cannot be replaced by quotient representatives, host equality, countable choice, or ambient completeness.
\end{proof}

\begin{theorem}[Hausdorff completion envelope sibling route]
\label{thm:hausdorff-completion-envelope-sibling-route}
A $\HausdorffCompletionEnvelopeUp$ consumer may hand its separated boundary to $\HausdorffUniformCompletionUp$ only through the displayed $\HausdorffSpaceUp$, $\SeparatedCompletionUp$, $\MetricCompletionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ rows of
$$
E=(H,S,M,W,D,R,L,T,K,P,N).
$$
The handoff contains no quotient-filter coordinate, representative-selection coordinate, host-equality coordinate, or ambient-completeness coordinate.
\end{theorem}
\begin{proof}
Apply \autoref{thm:hausdorff-completion-envelope-obligations}. It places the Hausdorff row $H$, separated-completion row $S$, metric-completion row $M$, stream row $W$, dyadic row $D$, regular-rational row $R$, and terminal Real row $L$ inside one displayed packet.

Next use \autoref{thm:hausdorff-completion-envelope-separated-metric-route}. The separated boundary $H,S$ is already carried through the metric and Real-facing route $M,W,D,R,L$.

The sibling $\HausdorffUniformCompletionUp$ consumer therefore reads the same separated boundary as its input surface rather than receiving a separate primitive. Since the carrier only has the displayed rows and the structural rows $T,K,P,N$, quotient filters, selected representatives, host equality, and ambient completeness remain outside the handoff.
\end{proof}

\begin{closurestatus}{\HausdorffCompletionEnvelopeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hausdorff-completion-envelope-carrier}, \autoref{thm:hausdorff-completion-envelope-obligations}, and \autoref{thm:hausdorff-completion-envelope-separated-metric-route} name the separated completion envelope surface for the L10 Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient filters, host equality, choice-selected representatives, or ambient completeness.}
  \upgradepath{Obligation closure requires the carrier route to be tied to the sibling completion obligation theorems and then exposed as a public chapter surface.}
  \constructivestory{A $\HausdorffCompletionEnvelopeUp$ packet is generated from Hausdorff separation, separated-completion boundary, metric-completion route, finite stream windows, dyadic tolerance, regular-rational readback, Real seal, transport, replay, provenance, and local NameCert rows.}
\end{closurestatus}
