\chapter{A Concrete Naming Certificate for $\DNAWindowSixTranslationBoundaryUp$}
\label{ch:concrete-instances-dna-window-six-translation-boundary-namecert}
\origin{ai}

The $\DNAWindowSixTranslationBoundaryUp$ packet realizes the local translation-boundary branch of \autoref{subsec:philosophy-dna-window-six-boundary-tiles} as finite NameCert data. It consumes the codon-window and stop-tile boundary analysis in the source vision, the curated code-boundary ledger of \autoref{ch:concrete-instances-14105_bioreality_q_six_leave_one_code_boundary_ledger-namecert}, and the trigger-threshold surface of \autoref{ch:concrete-instances-dna-window-six-trigger-threshold-namecert}. The packet names only a finite window-six translation-boundary carrier; biological translation realization, universality, protein function, and evolutionary mechanism remain outside the BEDC kernel packet.

\begin{definition}[DNA window-six translation-boundary carrier]
\label{def:dna-window-six-translation-boundary-carrier}
A $\DNAWindowSixTranslationBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,S,T,L,R,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the codon $Q_{6}$ window row recording the six-bit coordinate readback for the inspected codon window.
\item $S$ is the stop-tile boundary row recording the local halt boundary and continuation-corner split from the source vision.
\item $T$ is the translation-classifier row supplied by external biological bridge data.
\item $L$ is the curated code-boundary ledger row inherited from $\BioRealityQSixLeaveOneCodeBoundaryLedgerUp$.
\item $R$ is the release-factor or release-mechanism row that records which external recognition boundary is being tested.
\item $V$ is the finite validation row recording which observed table, organismal code row, or assay class is used for the test.
\item $H$ records componentwise $\hsame$ transport for the window, tile, classifier, ledger, release, and validation rows.
\item $C$ records displayed $\Cont$ replay of the boundary read through those rows.
\item $P$ records $\Pkg$ provenance over the source vision, the bio-reality ledger sibling, $\DNAWindowSixTriggerThresholdUp$, $\BHist$, $\hsame$, $\Cont$, and local naming rows.
\item $N$ is the local $\NameCert_{\DNAWindowSixTranslationBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for biological necessity, global identification of the genetic code with the window-six fold, protein-folding realization, universal stop assignment, hidden BEDC channel tokens, or untested mechanism.
\end{definition}

\begin{theorem}[DNA window-six translation-boundary obligations]
\label{thm:dna-window-six-translation-boundary-obligations}
For the carrier of \autoref{def:dna-window-six-translation-boundary-carrier}, the local $\NameCert_{\DNAWindowSixTranslationBoundaryUp}$ surface consists exactly of codon-window exposure, stop-tile boundary visibility, external translation-classifier disclosure, curated code-ledger preservation, release-boundary test exposure, finite validation-row visibility, componentwise transport, displayed continuation replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the accepted packet $B=(Q,S,T,L,R,V,H,C,P,N)$. The rows $Q,S,T$ expose the finite codon window, the local translation boundary, and the external classifier before any biological reading is admitted.

The ledger and release rows $L,R$ keep the packet anchored to the bio-reality boundary sibling and to a displayed recognition test. The validation row $V$ records the observed table or assay class being tested, so the packet has a falsifiable contact surface rather than a kernel claim of biological necessity.

The structural rows $H,C,P,N$ transport, replay, source, and name exactly the displayed boundary route. Since no further coordinate is present, the carrier cannot export global window-six identity, universal stop assignment, protein-folding realization, hidden channel tokens, or untested mechanism.
\end{proof}

\begin{theorem}[DNA window-six translation-boundary sibling handoff]
\label{thm:dna-window-six-translation-boundary-sibling-handoff}
Every accepted $\DNAWindowSixTranslationBoundaryUp$ read that reaches a translation-boundary consumer must first expose the source-vision stop-tile row of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, the curated code-boundary ledger row of \autoref{ch:concrete-instances-14105_bioreality_q_six_leave_one_code_boundary_ledger-namecert}, and the finite trigger-threshold row of \autoref{ch:concrete-instances-dna-window-six-trigger-threshold-namecert}. The handoff is therefore a concrete finite boundary-tile NameCert route, not a narrative-only direction.
\end{theorem}
\begin{proof}
Use \autoref{def:dna-window-six-translation-boundary-carrier}. The source-vision row is carried by $S$, the code-boundary ledger is carried by $L$, and the trigger-facing finite boundary read is recorded in the same package provenance $P$.

Now apply \autoref{thm:dna-window-six-translation-boundary-obligations}. The local NameCert requires those rows before the translation-boundary consumer can read $N$. Hence the consumer sees the source vision, the bio-reality ledger sibling, and the trigger-threshold sibling as displayed packet data rather than as detached prose.
\end{proof}

\falsifiablePrediction{An accepted $\DNAWindowSixTranslationBoundaryUp$ packet must expose a finite validation row naming the observed code table, organismal code row, or release-factor assay class before it can export a translation-boundary reading.}

\independenceWitness{bioreality-q-six-leave-one-code-boundary-ledger, dna-window-six-trigger-threshold, synonymous-transition: the $\DNAWindowSixTranslationBoundaryUp$ packet is not bijective to any listed sibling because it jointly carries codon-window, stop-tile, external translation-classifier, curated code-ledger, release-boundary, validation, transport, replay, provenance, and local naming rows.}

The Lean follow-up must provide $\Nontrivial\ \DNAWindowSixTranslationBoundaryUp$ and $\FieldFaithful\ \DNAWindowSixTranslationBoundaryUp$ TasteGate instances before this packet can move beyond seed closure.

\closureat{DNAWindowSixTranslationBoundaryUp}{seedStr}

\begin{closurestatus}{\DNAWindowSixTranslationBoundaryUp}
  \constructivestory{A $\DNAWindowSixTranslationBoundaryUp$ packet is generated from codon Q-six window rows, stop-tile boundary rows, external translation-classifier rows, curated code-boundary ledgers, release-boundary tests, finite validation rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dna-window-six-translation-boundary-carrier}, \autoref{thm:dna-window-six-translation-boundary-obligations}, and \autoref{thm:dna-window-six-translation-boundary-sibling-handoff} specify the finite translation-boundary carrier and sibling route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim biological-code necessity, global window-six identity, universal stop assignment, protein-folding realization, hidden BEDC channel tokens, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean carrier encoding, TasteGate nontriviality, field faithfulness, validation-row exactness, sibling-route preservation, transport, replay, provenance, and local naming.}
\end{closurestatus}
