\chapter{A Concrete Naming Certificate for $\CauchyCompletionMonadicityUp$}
\label{ch:concrete-instances-cauchy-completion-monadicity-namecert}
\origin{human}

Following Mac Lane on monads and Eilenberg--Moore comparison, together with Bishop--Bridges constructive completion, the $\CauchyCompletionMonadicityUp$ packet records the finite BEDC surface where the L10 completion monad, its algebra action, the Kleisli route, the universal-property row, and the dense-embedding unit route are compared as one NameCert boundary. The packet reads \autoref{ch:concrete-instances-cauchycompletionmonad-namecert}, \autoref{ch:concrete-instances-cauchy-completion-kleisli-namecert}, \autoref{ch:concrete-instances-cauchy-completion-algebra-namecert}, \autoref{ch:concrete-instances-completionuniversalproperty-namecert}, \autoref{ch:concrete-instances-metric-completion-dense-embedding-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}. It names the comparison surface only; it does not assert quotient completion equality, selected limits, host equality of completed objects, countable choice, ambient completeness, or full $\RealUp$ completeness.

\begin{definition}[CauchyCompletionMonadicity carrier]
\label{def:cauchy-completion-monadicity-carrier}
A $\CauchyCompletionMonadicityUp$ carrier is a finite $\BHist$ packet
$$
M=(T,A,K,U,D,W,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\CauchyCompletionMonadUp$ completion-monad row, displaying the unit and bind schedule before any algebra or comparison read is consumed.
\item $A$ is the $\CauchyCompletionAlgebraUp$ action row, recording the Eilenberg--Moore algebra action over the displayed completion route.
\item $K$ is the $\CauchyCompletionKleisliUp$ row, exposing the unit, bind, and reassociated-bind consumer route.
\item $U$ is the $\CompletionUniversalPropertyUp$ row, carrying the extension and uniqueness ledger used by comparison consumers.
\item $D$ is the $\MetricCompletionDenseEmbeddingUp$ unit route, displaying the dense source-to-completion image before the algebra or universal-property read is exported.
\item $W$ is the finite $\StreamNameUp$ window row used by the monad, algebra, Kleisli, universal-property, and dense-embedding rows.
\item $R$ is the $\RegSeqRatUp$ regular-rational readback row attached to the same finite windows.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare completion-facing reads at the same finite precision.
\item $E$ is the terminal $\RealUp$ readback seal reached only after $W,R,Q$ have all been displayed.
\item $H$ records componentwise $\hsame$ transport for the monad, algebra action, Kleisli route, universal-property row, dense-embedding unit route, readback rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from comparison requests through $T,A,K,U,D,W,R,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionMonadicityUp$, $\CauchyCompletionMonadUp$, $\CauchyCompletionAlgebraUp$, $\CauchyCompletionKleisliUp$, $\CompletionUniversalPropertyUp$, $\MetricCompletionDenseEmbeddingUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionMonadicityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,A,K,U,D,W,R,Q,E,H,C,P,N$. The carrier has no coordinate for quotient completion classes, selected limit representatives, host equality of completed objects, countable-choice schedules, ambient completeness, full $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[CauchyCompletionMonadicity NameCert obligations]
\label{thm:cauchy-completion-monadicity-obligations}
For every accepted $\CauchyCompletionMonadicityUp$ carrier
$$
M=(T,A,K,U,D,W,R,Q,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionMonadicityUp}$ surface consists exactly of carrier admission, completion-monad visibility, algebra-action exposure, Kleisli-route exposure, universal-property handoff, dense-embedding unit visibility, StreamName--RegSeqRat--DyadicRatCore--Real readback discipline, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-completion-monadicity-carrier}. The displayed tuple lists every row available to the classifier, so local comparison can inspect only the completion monad, algebra action, Kleisli route, universal-property row, dense-embedding unit route, readback rows, transport, replay, provenance, and local naming.

The monadicity-facing rows are read in order. The monad row $T$ displays the unit and bind schedule, the algebra row $A$ records the Eilenberg--Moore action over that schedule, and the Kleisli row $K$ keeps unit, bind, and reassociated-bind consumers on the same finite route.

The universal and dense rows then bind the comparison surface. The row $U$ supplies extension and uniqueness data, while $D$ supplies the dense source-to-completion unit route used before the comparison is exported.

Finally the readback and structural rows close the NameCert surface. The rows $W,R,Q,E$ give finite windows, regular rational readback, dyadic tolerances, and the terminal Real seal; the rows $H,C,P,N$ transport, replay, source, and name exactly that packet. Since no excluded coordinate occurs, no additional local obligation is available.
\end{proof}

\begin{theorem}[CauchyCompletionMonadicity comparison surface]
\label{thm:cauchy-completion-monadicity-comparison-surface}
Every comparison consumer of an accepted $\CauchyCompletionMonadicityUp$ carrier factors through the finite route
$$
T,A,K,U,D \longmapsto W \longmapsto R \longmapsto Q \longmapsto E \longmapsto H,C,P,N .
$$
Thus the completion-monad route, the algebra action, the Kleisli route, the universal-property row, and the dense-embedding unit route are compared only after the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ readback surface has been displayed. The comparison exports no quotient completion equality, selected limit, host equality of completed objects, countable choice, ambient completeness, or full $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the monad and algebra rows. The row $T$ supplies the displayed completion transformer, and $A$ reads its algebra action only as a row over that transformer.

Next attach the Kleisli and universal-property rows. The row $K$ exposes the unit, bind, and reassociated-bind route, while $U$ records the extension and uniqueness ledger for completion-facing consumers.

Now read the dense-embedding unit route $D$. It displays the source-to-completion image before the comparison reaches any terminal seal, so the route is a visible unit comparison rather than a selected representative.

Finally consume the readback and structural rows. The finite window $W$, regular readback $R$, dyadic tolerance ledger $Q$, and Real seal $E$ precede transport, replay, provenance, and naming through $H,C,P,N$. Since the carrier contains no coordinate for the excluded objects, the comparison surface cannot export them.
\end{proof}

\closureat{CauchyCompletionMonadicityUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionMonadicityUp}
  \constructivestory{A $\CauchyCompletionMonadicityUp$ packet is generated from a CauchyCompletionMonad route, CauchyCompletionAlgebra action row, CauchyCompletionKleisli route, CompletionUniversalProperty row, MetricCompletionDenseEmbedding unit route, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance ledger, terminal Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-monadicity-carrier}, \autoref{thm:cauchy-completion-monadicity-obligations}, and \autoref{thm:cauchy-completion-monadicity-comparison-surface} seed the finite monadicity comparison boundary for the L10 completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected limits, host equality of completed objects, countable choice, ambient completeness, full $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, completion-monad visibility, algebra-action exposure, Kleisli-route exposure, universal-property handoff, dense-embedding unit visibility, readback discipline, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCompletionMonadicityUp.}
\end{closurestatus}
