\chapter{A Concrete Naming Certificate for $\YoungIntegrationUp$}
\label{ch:concrete-instances-young-integration-namecert}
\origin{human}

Following Young's integration theorem and Bishop--Bridges constructive analysis, the $\YoungIntegrationUp$ packet records the finite dyadic route for integrating one Holder-controlled path against another. It sits beside the Holder-continuity surface of \autoref{ch:concrete-instances-holder-continuity-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, and the tagged-mesh Riemann integral boundary of \autoref{ch:concrete-instances-riemannintegral-namecert}. The chapter names only a finite partition-and-error certificate; it does not import host path spaces, quotient equality of functions, selected limiting partitions, countable choice, measure completion, or ambient completeness of $\RealUp$.

\begin{definition}[Young integration finite partition carrier]
\label{def:young-integration-finite-partition-carrier}
A $\YoungIntegrationUp$ carrier is a finite $\BHist$ packet
$$
Y=(F,G,A,B,W,V,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the integrand path row, read through a $\HolderContinuityUp$ packet with its source interval observations, target Real estimates, rational exponent, and displayed Holder constant.
\item $G$ is the integrator path row, read through a second $\HolderContinuityUp$ packet with its own source interval observations, target Real estimates, rational exponent, and displayed Holder constant.
\item $A$ and $B$ are the two Holder exponent ledgers. They include the finite comparison row witnessing that the displayed exponents have a Young margin for the dyadic partition family.
\item $W$ is the dyadic partition-window row. It lists the inspected endpoints, dyadic mesh refinements, cell order, adjacent-cell handoffs, and the finite cells on which the integration read is allowed to form sums.
\item $V$ is the cross-variation tolerance ledger. It records the cellwise oscillation products, Holder-bound products, Young-margin comparisons, and finite sum-difference tolerances consumed by the route.
\item $D$ is the $\DyadicRatCoreUp$ ledger for endpoint radii, mesh widths, exponent-comparison margins, oscillation products, and final error bounds.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational trace of dyadic Young sums.
\item $E$ is the terminal $\RealUp$ seal for the integral value, reached only after the two Holder rows, dyadic windows, cross-variation ledger, dyadic tolerances, and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two Holder paths, exponent ledgers, partition windows, cross-variation ledger, dyadic ledger, readback, Real seal, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay from a Young-integration request through Holder admission, dyadic partition windows, cross-variation tolerances, regular rational readback, and the Real seal.
\item $P$ is the $\Pkg$ provenance over $\YoungIntegrationUp$, $\HolderContinuityUp$, $\DyadicPartitionUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\RiemannIntegralUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\YoungIntegrationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,G,A,B,W,V,D,R,E,H,C,P,N$. It has no coordinate for an ambient path space, quotient equality of functions, a selected sequence of partitions, a hidden limiting argument, countable choice, measure completion, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Young integration NameCert obligations]
\label{thm:young-integration-namecert-obligations}
For every accepted $\YoungIntegrationUp$ carrier $Y=(F,G,A,B,W,V,D,R,E,H,C,P,N)$, the local $\NameCert_{\YoungIntegrationUp}$ surface is exhausted by admission of two $\HolderContinuityUp$ path rows, exponent-margin comparison, dyadic partition-window formation, cross-variation tolerance accounting, $\DyadicRatCoreUp$ exactness, $\RegSeqRatUp$ readback, $\RealUp$ sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No accepted consumer may replace these rows by host path spaces, quotient equality of functions, selected limiting partitions, countable choice, measure completion, or ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:young-integration-finite-partition-carrier}. The rows $F$ and $G$ expose the two Holder-controlled paths, and $A,B$ expose only the finite exponent and Young-margin comparisons attached to those rows.

The partition and tolerance data are then forced. The row $W$ lists the dyadic windows available to the route, while $V$ records the cross-variation products and sum-difference tolerances over exactly those windows.

The terminal read is $D,R,E$. Dyadic exactness is read through $D$, the regular rational trace through $R$, and the Real integral seal through $E$ only after the preceding rows have been consumed.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed route. Since the excluded objects have no carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Young integration dyadic error budget]
\label{thm:young-integration-dyadic-error-budget}
Every accepted $\YoungIntegrationUp$ read that reaches the $\RealUp$ seal factors through the finite dyadic budget
$$
\HolderContinuityUp,\HolderContinuityUp \longmapsto \DyadicPartitionUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The row $V$ must display the cross-variation tolerance consumed between the partition windows and the rational readback. Therefore the exported integral value is a finite dyadic Young-sum seal, not a Riemann-integral replacement, a measure-completion integral, a quotient path equality, a selected limiting partition, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the two Holder rows. Their displayed exponents and constants are read through $F,G,A,B$, so the route has only the finite power-law data needed to bound oscillations on dyadic cells.

Next read the dyadic partition windows. The row $W$ fixes the cells, endpoints, mesh refinements, and adjacent-cell handoffs before any sum-difference comparison is requested.

The error budget is the pair $V,D$. The cross-variation ledger $V$ records the oscillation products and Young-margin comparisons, and the dyadic ledger $D$ records the exact rational tolerances used to compare any two displayed sums.

The readback and seal are downstream. The regular sequence row $R$ is the only rational trace exported from the finite budgets, and $E$ is the only Real seal. Thus the consumer cannot obtain any of the excluded host-level or choice-level objects from the packet.
\end{proof}

\begin{theorem}[Young integration Riemann boundary]
\label{thm:young-integration-riemann-boundary}
Every $\RiemannIntegralUp$ consumer of an accepted $\YoungIntegrationUp$ packet reads it only as a finite tagged-mesh boundary: two Holder path rows, a dyadic partition-window row, a cross-variation tolerance ledger, dyadic exactness, regular rational readback, Real sealing, transport, replay, provenance, and local naming. The consumer receives no independent Riemann-integral certificate, no Darboux gap claim, no quotient equality of integrands, no measure-completion object, and no selected mesh-limit principle.
\end{theorem}
\begin{proof}
The only Riemann-facing data in the carrier are the displayed dyadic windows and finite sum budgets. The two Holder path rows provide values to be sampled, while $W$ supplies the finite tagged-mesh boundary.

The cross-variation ledger is not a Darboux or measure-theoretic claim. It records only the tolerance comparisons needed for the Young-sum route before the regular rational readback is sealed as a Real value.

The provenance row may name $\RiemannIntegralUp$ as a consumer boundary, but the local certificate remains $F,G,A,B,W,V,D,R,E,H,C,P,N$. Therefore a Riemann-integral consumer receives a finite boundary row rather than any independent integral theorem or hidden limiting principle.
\end{proof}

\falsifiablePrediction{An accepted $\YoungIntegrationUp$ packet is refuted if a consumer reaches the $\RealUp$ seal while omitting either $\HolderContinuityUp$ path row, the dyadic partition-window row $W$, the cross-variation ledger $V$, the $\DyadicRatCoreUp$ ledger $D$, or the $\RegSeqRatUp$ readback row $R$.}

\independenceWitness{HolderContinuity, DyadicPartition, DyadicRatCore, RegSeqRat, Real, RiemannIntegral: none is bijective with $\YoungIntegrationUp$ because the packet jointly carries two Holder paths, Young-margin exponent rows, dyadic partition windows, cross-variation tolerances, dyadic exactness, regular rational readback, a Real seal, transport, replay, provenance, and local naming.}

\closureat{YoungIntegrationUp}{seedStr}

\begin{closurestatus}{\YoungIntegrationUp}
  \constructivestory{A $\YoungIntegrationUp$ packet is generated from two HolderContinuityUp path rows, exponent-margin ledgers, dyadic partition windows, cross-variation tolerance accounting, DyadicRatCore exactness, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:young-integration-finite-partition-carrier}, \autoref{thm:young-integration-namecert-obligations}, \autoref{thm:young-integration-dyadic-error-budget}, and \autoref{thm:young-integration-riemann-boundary} seed the finite dyadic Young-integration route over HolderContinuityUp, DyadicPartitionUp, DyadicRatCoreUp, RegSeqRatUp, RealUp, and RiemannIntegralUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host path spaces, quotient equality of functions, selected limiting partitions, countable choice, measure completion, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked two-path admission, exponent-margin comparison, dyadic partition-window formation, cross-variation tolerance accounting, dyadic exactness, regular rational readback, Real-seal nonescape, and structural transport for BEDC.Derived.YoungIntegrationUp.}
\end{closurestatus}
