\chapter{A Concrete Naming Certificate for $\DenjoyYoungSaksUp$}
\label{ch:concrete-instances-denjoy-young-saks-namecert}
\origin{human}

Following Saks and Bishop--Bridges constructive real analysis, the $\DenjoyYoungSaksUp$ packet records the finite boundary at which a real-valued interval map can expose upper and lower Dini-derivative rows without importing the classical almost-everywhere Denjoy--Young--Saks theorem. It sits next to the $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\StreamNameUp$ observation window of \autoref{ch:concrete-instances-streamname-namecert}, and the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}. The packet is a finite classification boundary for displayed Dini rows, oscillation windows, regular-rational readback, and terminal Real seals; it is not a measure theorem, an almost-everywhere classifier, or a host-real differentiability principle.

\begin{definition}[Denjoy--Young--Saks finite Dini carrier]\label{def:denjoy-young-saks-carrier}
A $\DenjoyYoungSaksUp$ carrier is a finite $\BHist$ packet
$$
Y=(I,F,U,L,O,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the inspected interval row, listing the finitely presented source intervals and endpoint cells on which the local boundary is read.
\item $F$ is the function-observation row, recording the finite source and target windows used to compare difference quotients.
\item $U$ is the upper Dini row, storing the displayed upper right, upper left, and two-sided upper derivative bounds visible at the inspected windows.
\item $L$ is the lower Dini row, storing the corresponding lower right, lower left, and two-sided lower derivative bounds.
\item $O$ is the oscillation-window row, recording the finite alternation and stabilization tests used to classify a displayed window as one of the Dini-boundary cases.
\item $S$ is the $\StreamNameUp$ observation schedule opened by $I,F,O$ and no hidden stream coordinates.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational data extracted from the finite stream windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger supporting the difference-quotient comparisons and oscillation bounds.
\item $E$ is the terminal $\RealUp$ seal row, reached only after the interval, function-observation, Dini, oscillation, stream, readback, and dyadic rows have been exposed.
\item $H$ records componentwise $\hsame$ transport for intervals, function observations, Dini rows, oscillation windows, stream schedules, regular readbacks, dyadic ledgers, Real seals, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the inspected interval and function rows through $U,L,O,S,R,D$ and into the Real seal $E$.
\item $P$ is the $\Pkg$ provenance over $\DenjoyYoungSaksUp$, $\RealUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DenjoyYoungSaksUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $I,F,U,L,O,S,R,D,E,H,C,P,N$. It has no coordinate for measure-null exceptional sets, almost-everywhere validity, selected derivatives, quotient real equality, host real order trichotomy, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[Denjoy--Young--Saks finite boundary obligations]\label{thm:denjoy-young-saks-namecert-obligations}
For every accepted $\DenjoyYoungSaksUp$ carrier $Y=(I,F,U,L,O,S,R,D,E,H,C,P,N)$, the local $\NameCert_{\DenjoyYoungSaksUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the inspected interval, function-observation, upper Dini, lower Dini, oscillation-window, stream-schedule, regular-readback, dyadic-ledger, Real-seal, transport, replay, provenance, and local naming rows;
\item interval and observation exactness, requiring every Dini comparison to read its source cell from $I$ and its finite function window from $F$ before any derivative row is accepted;
\item upper and lower Dini-row exactness, requiring $U$ and $L$ to store only the finite upper and lower derivative bounds justified by the displayed difference-quotient windows;
\item oscillation-window classification, requiring $O$ to record the finite alternation, stabilization, and gap tests that separate the visible Dini-boundary cases;
\item stream, readback, and dyadic exactness, requiring $S,R,D$ to expose only the finite observations, regular rational readbacks, and dyadic tolerance rows demanded by $I,F,U,L,O$;
\item Real seal nonescape, requiring $E$ to remain downstream of $I,F,U,L,O,S,R,D$ and never to serve as a selected derivative, a host real equality witness, or an almost-everywhere theorem;
\item componentwise transport, replay, provenance, and local naming, requiring $H,C,P,N$ to preserve exactly the displayed finite route.
\end{enumerate}
No $\DenjoyYoungSaksUp$ obligation is stored outside these rows, and the packet makes no claim that the classical Denjoy--Young--Saks alternatives hold almost everywhere.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:denjoy-young-saks-carrier}. The accepted packet displays exactly the inspected interval row $I$, function-observation row $F$, upper and lower Dini rows $U,L$, oscillation row $O$, stream schedule $S$, regular readback $R$, dyadic ledger $D$, Real seal $E$, and structural rows $H,C,P,N$.

Interval and observation exactness follow from the row order. A Dini comparison first reads the source cell in $I$ and the finite function-observation window in $F$; only then may it inspect the upper row $U$, lower row $L$, or oscillation row $O$ attached to that window.

The stream, regular-readback, and dyadic rows are downstream of the same finite windows. The schedule $S$ opens only the observations demanded by $I,F,O$, the row $R$ records the resulting regular rational readback, and $D$ stores the tolerance comparisons needed for the displayed difference-quotient bounds.

Finally, the Real seal $E$ is terminal for this finite boundary route. The transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$ preserve the same packet, so measure-null exceptional sets, almost-everywhere validity, selected derivatives, quotient real equality, trichotomy, countable choice, and ambient completeness cannot become local obligations.
\end{proof}

\begin{theorem}[Denjoy--Young--Saks Real seal nonescape]\label{thm:denjoy-young-saks-real-seal-nonescape}
Every $\RealUp$, $\RegSeqRatUp$, or $\StreamNameUp$ consumer of an accepted $\DenjoyYoungSaksUp$ carrier reads the displayed route
$$
I,F,U,L,O,S,R,D,E,H,C,P,N .
$$
Consequently the consumer may inspect finite interval cells, function observations, upper and lower Dini rows, oscillation windows, StreamName schedules, RegSeqRat readbacks, DyadicRatCore tolerance ledgers, a terminal Real seal, componentwise transport, replay, provenance, and local naming. It cannot read a measure structure, an almost-everywhere assertion, a selected derivative, quotient real equality, host real trichotomy, countable choice, or ambient completeness from the packet.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:denjoy-young-saks-carrier}. Its Real-facing and readback-facing rows are exactly $S,R,D,E$ together with the preceding interval, function, Dini, and oscillation rows $I,F,U,L,O$ and the structural rows $H,C,P,N$.

The route reaches $E$ only after the finite Dini and oscillation boundary has been displayed. Thus any consumer that asks for a Real seal or regular rational readback must already have passed through the interval cells, function observations, upper and lower Dini rows, oscillation windows, stream schedule, and dyadic tolerance ledger.

Since the carrier has no row for measure, almost-everywhere validity, selected derivatives, quotient real equality, trichotomy, countable choice, or ambient completeness, none of those objects can be read by a downstream consumer.
\end{proof}

\begin{theorem}[Denjoy--Young--Saks oscillation-window induction]\label{thm:denjoy-young-saks-oscillation-window-induction}
For an accepted $\DenjoyYoungSaksUp$ carrier $Y=(I,F,U,L,O,S,R,D,E,H,C,P,N)$, induction over the finite oscillation-window row $O$ preserves the separation between the upper Dini row $U$ and the lower Dini row $L$. At every displayed stage the packet remains a finite boundary classifier over the rows of \autoref{def:denjoy-young-saks-carrier}; the induction cannot promote the packet to an almost-everywhere measure theorem, cannot select a derivative, and cannot export a host-real differentiability principle.
\end{theorem}
\begin{proof}
Induct over the displayed list of oscillation windows in $O$. The empty row has no Dini comparison to transport, so the upper and lower rows remain separated by the carrier projection.

For the step, assume the previously displayed windows preserve the separation of $U$ and $L$. The next window is admitted only through the oscillation-window classification row in \autoref{thm:denjoy-young-saks-namecert-obligations}, so it may inspect the finite alternation, stabilization, and gap tests attached to that window but cannot rewrite the carrier outside $I,F,U,L,O,S,R,D,E,H,C,P,N$.

The Real-seal nonescape theorem \autoref{thm:denjoy-young-saks-real-seal-nonescape} keeps every downstream read behind the same finite route. Thus adjoining the next oscillation window preserves the visible upper/lower Dini separation and leaves measure-null exceptional sets, almost-everywhere validity, selected derivatives, quotient real equality, trichotomy, countable choice, and ambient completeness outside the packet.
\end{proof}

\falsifiablePrediction{Every $\DenjoyYoungSaksUp$ Real-facing or readback-facing read factors through finite interval cells, function-observation windows, upper and lower Dini rows, oscillation windows, StreamName schedules, RegSeqRat readbacks, DyadicRatCore tolerance ledgers, a terminal RealUp seal, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{real, regseqrat, streamname, dyadicratcore: $\DenjoyYoungSaksUp$ is not bijective to any listed sibling because it jointly carries upper and lower Dini rows, oscillation-window classification, regular-rational readback, dyadic tolerance data, and a terminal Real seal in one finite boundary packet.}

\closureat{DenjoyYoungSaksUp}{seedStr}

\begin{closurestatus}{\DenjoyYoungSaksUp}
  \constructivestory{A $\DenjoyYoungSaksUp$ packet is generated from inspected interval cells, function-observation windows, upper and lower Dini rows, oscillation-window classifications, StreamName schedules, RegSeqRat readbacks, DyadicRatCore tolerance ledgers, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:denjoy-young-saks-carrier}, \autoref{thm:denjoy-young-saks-namecert-obligations}, and \autoref{thm:denjoy-young-saks-real-seal-nonescape} seed the finite Denjoy--Young--Saks boundary route over Dini rows, oscillation windows, regular-rational readback, dyadic tolerance rows, and terminal Real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close the classical almost-everywhere Denjoy--Young--Saks theorem, measure-null exceptional sets, selected derivatives, quotient real equality, trichotomy, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Dini-row exactness, oscillation-window classification, stream-readback-dyadic exactness, Real seal nonescape, componentwise transport, replay, provenance, and local naming for BEDC.Derived.DenjoyYoungSaksUp.}
\end{closurestatus}
