\chapter{A Concrete Naming Certificate for $\QuotientLeakageMarkovUp$}
\label{ch:concrete-instances-quotient-leakage-markov-namecert}
\origin{ai}

The $\QuotientLeakageMarkovUp$ packet realizes the quotient leakage transition matrix of \autoref{thm:philosophy-quotient-leakage-transition-matrix} as finite NameCert data. It consumes the DNA window-six boundary-tile source of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, the codon-window carrier of \autoref{ch:concrete-instances-codon-six-bit-window-namecert}, the boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the six-boundary coverage route of \autoref{ch:concrete-instances-six-boundary-tile-coverage-namecert}, and the translation-boundary packet of \autoref{ch:concrete-instances-dna-window-six-translation-boundary-namecert}. The packet names a finite six-state Markov ledger only; it is not a biological stochastic model, empirical evolutionary claim, host quotient-codon semantics, or unrestricted state-space enumeration.

\begin{definition}[QuotientLeakageMarkov carrier]
\label{def:quotient-leakage-markov-carrier}
A $\QuotientLeakageMarkovUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,T,O,E,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the six-state orbit row listing $\mathrm{AGR}$, $\mathrm{Anchor}_{6}$, $\mathrm{StopStart}_{6}$, $\mathrm{UUR}$, $\mathrm{CUR}$, and $\mathrm{CUY}$.
\item $T$ is the transient transition-matrix row of \autoref{thm:philosophy-quotient-leakage-transition-matrix}, with entries read as exact rational finite counts.
\item $O$ is the outside-probability row recording $1/3,1/3,1/3,1/6,1/2,2/3$ for the six displayed states.
\item $E$ is the expected-exit ledger row recording the rational exit values of \autoref{thm:philosophy-quotient-expected-exit-times}.
\item $W$ is the finite window-six source row tying the orbit states to the codon-window and boundary-tile siblings.
\item $H$ records componentwise $\hsame$ transport for the state, transition, outside-probability, exit-ledger, source, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the finite Markov read through $S,T,O,E,W,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\QuotientLeakageMarkovUp$, $\CodonSixBitWindowUp$, $\DnaWindowSixBoundaryTileUp$, $\SixBoundaryTileCoverageUp$, $\DNAWindowSixTranslationBoundaryUp$, the source vision of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\QuotientLeakageMarkovUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,T,O,E,W,H,C,P,N$. It has no coordinate for biological transition realization, hidden codon quotient semantics, empirical fitness, unbounded simulation, or a completed stochastic process.
\end{definition}

\begin{theorem}[QuotientLeakageMarkov NameCert obligations]
\label{thm:quotient-leakage-markov-namecert-obligations}
For the carrier of \autoref{def:quotient-leakage-markov-carrier}, the local $\NameCert_{\QuotientLeakageMarkovUp}$ surface consists exactly of six-state exposure, transition-matrix exactness, outside-probability preservation, expected-exit ledger exposure, window-six sibling routing, componentwise transport, displayed replay, provenance, and local naming. Every accepted read preserves the outside probabilities displayed in \autoref{thm:philosophy-quotient-leakage-rates}.
\end{theorem}
\begin{proof}
Project the accepted carrier $Q=(S,T,O,E,W,H,C,P,N)$. The state row $S$ fixes the six orbit states, and the transition row $T$ is the only source of one-bit flip probabilities.

The outside-probability row $O$ is read from the outside column of $T$ and matches the finite rational list in \autoref{thm:philosophy-quotient-leakage-rates}. Thus an accepted packet cannot alter leakage rates without changing a displayed row.

The expected-exit row $E$ is downstream of the same finite matrix and records the rational ledger of \autoref{thm:philosophy-quotient-expected-exit-times}. The source row $W$ ties these finite state rows back to the codon-window, boundary-tile, coverage, and translation-boundary siblings.

Finally $H,C,P,N$ transport, replay, source, and name exactly those rows. Since no other coordinate is present, the NameCert surface cannot export biological mechanism, hidden quotient semantics, empirical fitness, unbounded simulation, or a completed stochastic process.
\end{proof}

\begin{theorem}[QuotientLeakageMarkov sibling dependency route]
\label{thm:quotient-leakage-markov-sibling-dependency-route}
Every accepted $\QuotientLeakageMarkovUp$ consumer first reads the finite codon-window source, boundary-tile classifier, six-boundary coverage route, and translation-boundary packet before it consumes the transition row $T$, outside row $O$, or expected-exit row $E$. The dependency route is
$$
\CodonSixBitWindowUp,\DnaWindowSixBoundaryTileUp,\SixBoundaryTileCoverageUp,\DNAWindowSixTranslationBoundaryUp
\longrightarrow
\QuotientLeakageMarkovUp .
$$
\end{theorem}
\begin{proof}
Use the provenance row $P$ and source row $W$ of \autoref{def:quotient-leakage-markov-carrier}. These rows name the finite codon-window and boundary-tile sources before the Markov matrix is admitted.

The transition row $T$ then reads the six-state quotient matrix of \autoref{thm:philosophy-quotient-leakage-transition-matrix}. The outside-probability row $O$ and expected-exit row $E$ are downstream ledger rows, so they cannot be consumed before the sibling source route has been displayed.

Transport and replay by $H$ and $C$ preserve this order, while $N$ names it locally. Hence the consumer receives a concrete dependency route rather than a detached numerical table.
\end{proof}

\falsifiablePrediction{Every accepted $\QuotientLeakageMarkovUp$ read preserves the displayed outside probabilities $1/3,1/3,1/3,1/6,1/2,2/3$ for $\mathrm{AGR}$, $\mathrm{Anchor}_{6}$, $\mathrm{StopStart}_{6}$, $\mathrm{UUR}$, $\mathrm{CUR}$, and $\mathrm{CUY}$.}

\independenceWitness{codon-six-bit-window, dna-window-six-boundary-tile, six-boundary-tile-coverage, dna-window-six-translation-boundary: $\QuotientLeakageMarkovUp$ is not bijective to any listed sibling because it jointly carries six orbit states, a rational transition matrix, outside probabilities, expected-exit ledgers, window-source routing, transport, replay, provenance, and local naming.}

The Lean follow-up must provide explicit $\Nontrivial\ \QuotientLeakageMarkovUp$ and $\FieldFaithful\ \QuotientLeakageMarkovUp$ TasteGate instances preserving $S,T,O,E,W,H,C,P,N$ as distinct displayed rows.

\closureat{QuotientLeakageMarkovUp}{seedStr}

\begin{closurestatus}{\QuotientLeakageMarkovUp}
  \constructivestory{A $\QuotientLeakageMarkovUp$ packet is generated from six orbit states, a rational transition matrix, outside-probability rows, expected-exit ledgers, a finite window-six source row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:quotient-leakage-markov-carrier}, \autoref{thm:quotient-leakage-markov-namecert-obligations}, and \autoref{thm:quotient-leakage-markov-sibling-dependency-route} specify the finite quotient-leakage Markov carrier and sibling dependency route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological transition realization, empirical evolutionary mechanism, hidden codon quotient semantics, unbounded simulation, completed stochastic processes, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, transition-matrix exactness, outside-probability preservation, expected-exit ledger exposure, sibling routing, transport, replay, provenance, and local naming for BEDC.Derived.QuotientLeakageMarkovUp.}
\end{closurestatus}
