\chapter{A Concrete Naming Certificate for $\UniformInverseModulusUp$}
\label{ch:concrete-instances-uniform-inverse-modulus-namecert}
\origin{human}

Following Bishop and Bridges, the $\UniformInverseModulusUp$ packet records compact inverse-modulus extraction from uniform homeomorphism data as finite NameCert data. It reads the homeomorphism and inverse-graph surface of \autoref{ch:concrete-instances-uniformhomeomorphism-namecert}, the compact finite-net rows of \autoref{ch:concrete-instances-compactmetric-namecert}, the graph and pointwise continuity rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the exported modulus interface of \autoref{ch:concrete-instances-uniformmodulus-namecert}, the metric-source and metric-target rows of \autoref{ch:concrete-instances-metric-space-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names the finite compact route that turns displayed inverse radii into a uniform inverse modulus; it is not a selected inverse function, host function equality, quotient real equality, open-cover compactness, or ambient completeness principle.

\begin{definition}[Uniform inverse modulus carrier]
\label{def:uniform-inverse-modulus-carrier}
A $\UniformInverseModulusUp$ carrier is a finite $\BHist$ packet
$$
I=(X,Y,F,G,E,N,R,M,T,H,C,P,A)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the compact source row, exposing the $\CompactMetricUp$ finite-net data used to cover the compact domain of the homeomorphism.
\item $Y$ is the target metric row, including the distance ledger into which the inverse-modulus estimate is reported.
\item $F$ is the $\UniformHomeomorphismUp$ graph row from $X$ to $Y$, carrying the forward graph and the homeomorphism naming data.
\item $G$ is the inverse graph row displayed by the same homeomorphism packet.
\item $E$ is the positive precision row, read through $\RealUp$ or $\RegSeqRatUp$ endpoint histories when the consumer presents a real tolerance.
\item $N$ is the finite net row of the compact source at the scale needed for the inverse-modulus extraction.
\item $R$ lists the pointwise inverse radius rows attached to the centers named by $N$.
\item $M$ is the finite radius-fold row, obtained only by folding the finite family $R$ over the index list of $N$.
\item $T$ is the target estimate row, combining inverse-graph exactness, finite-net coverage, the folded radius row, and the target metric triangle ledger.
\item $H$ records componentwise $\hsame$ transport for the compact source, target metric, homeomorphism graph, inverse graph, precision, finite-net, inverse-radius, radius-fold, and estimate rows.
\item $C$ records the displayed $\Cont$ replay route from compact homeomorphism data and pointwise inverse radii to the $\UniformModulusUp$ export.
\item $P$ records $\Pkg$ provenance over $\UniformInverseModulusUp$, $\UniformHomeomorphismUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\MetricSpaceUp$, $\RealUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $A$ is the local $\NameCert_{\UniformInverseModulusUp}$ row.
\end{enumerate}
The carrier exposes only displayed compact finite nets, graph rows, inverse-graph rows, endpoint readbacks, finite radius rows, componentwise transport, replay, provenance, and local naming. It has no coordinate for a host inverse function, selected inverse choice, host function equality, quotient real equality, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Uniform inverse modulus obligations]
\label{thm:uniform-inverse-modulus-obligations}
For every accepted $\UniformInverseModulusUp$ carrier
$$
I=(X,Y,F,G,E,N,R,M,T,H,C,P,A),
$$
the local $\NameCert_{\UniformInverseModulusUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the compact source, target metric, homeomorphism graph, inverse graph, precision, finite-net, inverse-radius, radius-fold, target-estimate, transport, replay, provenance, and local naming rows;
\item inverse-graph exactness, requiring every inverse read to pass through the displayed row $G$ attached to the homeomorphism row $F$;
\item compact finite-net handoff, requiring the compact source row $X$ and precision row $E$ to determine the finite row $N$ before any inverse radius is folded;
\item finite radius fold, requiring $M$ to be obtained only by folding the pointwise inverse radius rows $R$ over the finite indices of $N$;
\item target estimate, requiring $T$ to combine compact-net coverage, inverse-graph exactness, folded-radius data, and the target metric ledger;
\item transport, replay, and provenance, requiring $H,C,P,A$ to source the same displayed route componentwise;
\item nonescape, requiring the packet to export no host inverse function, selected inverse choice, host function equality, quotient real equality, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:uniform-inverse-modulus-carrier}. The projection exposes exactly the rows $X,Y,F,G,E,N,R,M,T,H,C,P,A$, so carrier admission and row inventory are finite.

The inverse read is confined to $G$. Since $G$ is listed as a row of the same homeomorphism packet that supplies $F$, inverse-graph exactness is consumed as displayed graph data rather than as host function equality or selected inverse choice.

The compact handoff reads $X$ and $E$ before radius data. These rows determine the finite net $N$, and the pointwise inverse radii in $R$ are indexed only by the centers listed by $N$.

Fold $R$ over that finite index list to obtain $M$. The target estimate row $T$ then combines the compact-net coverage, inverse-graph exactness, folded radius, and target metric triangle route. Finally $H,C,P,A$ transport, replay, source, and name the same route, so no excluded equality, choice, open-cover, trichotomy, or completeness coordinate is introduced.
\end{proof}

\begin{theorem}[Uniform inverse modulus compact handoff]
\label{thm:uniform-inverse-modulus-compact-handoff}
Every $\UniformModulusUp$ export from an accepted $\UniformInverseModulusUp$ carrier
$$
I=(X,Y,F,G,E,N,R,M,T,H,C,P,A)
$$
factors through the displayed finite route
$$
X,F,G,E \longmapsto N,R \longmapsto M,T \longmapsto H,C,P,A.
$$
Thus the inverse-modulus export is a compact finite-net and radius-fold handoff. It exports no host function equality, selected inverse choice, quotient real equality, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from a $\UniformModulusUp$ consumer of $I$. By \autoref{thm:uniform-inverse-modulus-obligations}, the consumer must read the compact source, homeomorphism graph, inverse graph, and precision rows before the finite-net row is available.

The only finite-net row is $N$, and the only pointwise inverse-radius inventory is $R$. Hence the consumer reaches the exported modulus row $M$ only after the finite fold over $R$ indexed by $N$.

The target estimate $T$ is downstream of that fold. It cannot be read as a host inverse function or as quotient equality of inverse values, because the carrier contains only displayed graph and metric-ledger rows.

Finally the structural rows $H,C,P,A$ transport, replay, source, and name the same compact route. Since the carrier contains no coordinate for selected inverse choice, trichotomy, open-cover compactness, or ambient completeness, the export factors through exactly the displayed finite-net and radius-fold handoff.
\end{proof}

\closureat{UniformInverseModulusUp}{seedStr}

\begin{closurestatus}{\UniformInverseModulusUp}
  \constructivestory{A $\UniformInverseModulusUp$ packet is generated from UniformHomeomorphism graph and inverse-graph rows, CompactMetric finite-net rows, ContinuousMap pointwise inverse-radius rows, UniformModulus export rows, MetricSpace distance ledgers, RealUp and RegSeqRat endpoint readbacks, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-inverse-modulus-carrier}, \autoref{thm:uniform-inverse-modulus-obligations}, and \autoref{thm:uniform-inverse-modulus-compact-handoff} seed the finite compact route from displayed inverse radii to a UniformModulus consumer.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient completeness, host inverse functions, selected inverse choice, quotient real equality, trichotomy, open-cover compactness, Lean verification, or standard bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, inverse-graph exactness, compact finite-net handoff, finite radius fold, target estimate, transport, replay, provenance, and local naming for BEDC.Derived.UniformInverseModulusUp.}
\end{closurestatus}
