\chapter{A Concrete Naming Certificate for $\LocatedCauchyFilterBasisUp$}
\label{ch:concrete-instances-located-cauchy-filter-basis-namecert}
\origin{human}

Following Bishop and Bridges, the $\LocatedCauchyFilterBasisUp$ packet names the finite located-basis interface used by the L10 Real and Completion route before the data are promoted to a located Cauchy filter. It refines the basis-generator surface of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert} and the located filter route of \autoref{ch:concrete-instances-located-cauchy-filter-namecert}; its finite reads pass through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and finally the downstream seal boundary of \autoref{ch:concrete-instances-real-namecert}. The chapter isolates the basis-level located witness, not a completed filter, quotient Cauchy name, selected real, or ambient completeness principle.

\begin{definition}[Located Cauchy filter basis carrier]
\label{def:cauchy-filter-basis-real-carrier}
A $\LocatedCauchyFilterBasisUp$ carrier is a finite $\BHist$ packet
$$
K=(B,L,S,R,D,W,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\CauchyFilterBasisUp$ row naming the finite basis elements and their common-refinement witnesses.
\item $L$ is the located-basis request row. It records the displayed dyadic ball request and the basis element that is asserted to meet it.
\item $S$ is the $\StreamNameUp$ finite-window row attached to the same located request.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger for the requested ball, inclusion comparison, and refinement radius.
\item $W$ is the finite witness row that the selected basis element meets the requested located ball after $S,R,D$ have been replayed.
\item $T$ is the tail-refinement row sending the located basis witness to the filter-level route of $\LocatedCauchyFilterUp$.
\item $E$ is the downstream $\RealUp$ seal boundary, reachable only after the basis, located request, finite windows, readback, tolerance, witness, and tail-refinement rows have been consumed.
\item $H$ records componentwise $\hsame$ transport for all displayed rows.
\item $C$ records displayed $\Cont$ replay from a located basis request through $B,L,S,R,D,W,T,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedCauchyFilterBasisUp$, $\CauchyFilterBasisUp$, $\LocatedCauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCauchyFilterBasisUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for completed filters, quotient stream equality, selected representatives, countable choice, trichotomy, host real equality, or completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Located Cauchy filter basis NameCert obligations]
\label{thm:cauchy-filter-basis-real-obligations}
For every accepted $\LocatedCauchyFilterBasisUp$ carrier $K=(B,L,S,R,D,W,T,E,H,C,P,N)$, the local $\NameCert_{\LocatedCauchyFilterBasisUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the finite basis row, located request row, stream windows, regular rational readback, dyadic tolerance ledger, located witness, tail-refinement handoff, seal boundary, transport, continuation, provenance, and local naming row;
\item located basis classification, requiring two accepted reads to agree precisely when their displayed requests admit a common basis refinement after $H$ transports the $B,L,S,R,D,W$ rows;
\item finite-window replay, requiring the located request to inspect only the windows in $S$ before the readback row $R$ and tolerance ledger $D$ are available;
\item witness exactness, requiring $W$ to show that the displayed basis element meets the requested dyadic ball using only the finite rows $S,R,D$;
\item tail refinement, requiring $T$ to hand the located basis witness to the $\LocatedCauchyFilterUp$ route before any real-facing seal can be read;
\item nonescape, excluding completed filters, quotient streams, selected representatives, countable choice, trichotomy, host real equality, and $\RealUp$ completeness.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-filter-basis-real-carrier}. The visible rows are exactly the finite basis data, located request, stream windows, rational readback, dyadic ledger, witness, tail refinement, seal boundary, transport, replay, provenance, and name.

The dependency anchors are the basis carrier of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert} and the located filter consumer of \autoref{ch:concrete-instances-located-cauchy-filter-namecert}. The finite observations, rational readbacks, tolerance ledgers, and terminal seal are read through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, and \autoref{ch:concrete-instances-real-namecert}.

Classifier comparison is componentwise. Transport by $H$ moves the basis row, located request, window row, readback row, tolerance ledger, and witness row to a common finite comparison surface, while $C$ replays the same order.

The located witness is finite. A request first reads $S$, then $R$, then $D$, and only then may $W$ certify that the displayed basis element meets the requested dyadic ball.

The tail-refinement row $T$ is the only route to $\LocatedCauchyFilterUp$, and $E$ is downstream from that route. Hence $P$ and $N$ cannot export completed filters, quotient streams, selected representatives, choice, trichotomy, host real equality, or real completeness.
\end{proof}

\begin{theorem}[Located Cauchy filter basis tail refinement]
\label{thm:cauchy-filter-basis-real-tail-refinement}
Let $K=(B,L,S,R,D,W,T,E,H,C,P,N)$ be an accepted $\LocatedCauchyFilterBasisUp$ carrier. Every located basis read factors through the finite route
$$
B,L \longmapsto S \longmapsto R \longmapsto D \longmapsto W \longmapsto T .
$$
The row $T$ then exposes the same witness as a filter-level located tail request for $\LocatedCauchyFilterUp$, with no bypass around the $\StreamNameUp$ finite windows, $\RegSeqRatUp$ readback, or $\DyadicRatCoreUp$ tolerance ledger.
\end{theorem}
\begin{proof}
Start with a located basis read. The rows $B$ and $L$ fix the displayed basis element and the dyadic ball request; neither row contains a sequence readback or a filter-level located-tail witness by itself.

Replay the continuation row $C$. The request reaches the finite window row $S$, then the regular rational readback row $R$, and then the dyadic tolerance ledger $D$.

Only after those finite rows have been consumed can $W$ certify the located hit. The row $T$ repackages that same finite witness for the $\LocatedCauchyFilterUp$ route, so the handoff cannot skip the StreamName, RegSeqRat, or DyadicRatCore ledgers.
\end{proof}

\begin{theorem}[Located Cauchy filter basis Real seal handoff]
\label{thm:cauchy-filter-basis-real-seal-handoff}
For every accepted $\LocatedCauchyFilterBasisUp$ carrier $K=(B,L,S,R,D,W,T,E,H,C,P,N)$, every $\RealUp$-facing read exposed by $P$ factors through the tail-refinement row $T$ and then through the seal boundary $E$. Equivalently, the only real-facing route visible in the packet is
$$
B,L,S,R,D,W \longmapsto T \longmapsto E \longmapsto H,C,P,N .
$$
Thus the Real seal is downstream of the located basis witness and cannot be read from basis elements, windows, rational readbacks, or dyadic tolerances alone.
\end{theorem}
\begin{proof}
Project the seal boundary row. The carrier lists $E$ after the finite basis route and after the tail-refinement row $T$, so the seal is not a coordinate of $B,L,S,R,D$, or $W$.

Replay the route by $C$. A real-facing request must first consume the basis row, located request, window row, readback row, tolerance ledger, and located witness, and must then pass through $T$.

Transport by $H$ preserves the same dependency order under classifier comparison. The provenance and local naming rows therefore record a downstream Real seal handoff rather than a selected limit, quotient equality, host real equality, or completeness witness.
\end{proof}

\begin{theorem}[Located Cauchy filter basis nonescape]
\label{thm:cauchy-filter-basis-real-nonescape}
An accepted $\LocatedCauchyFilterBasisUp$ packet cannot export any consumer route that reaches outside the finite rows
$$
B,L,S,R,D,W,T,E,H,C,P,N.
$$
In particular, any consumer asking for a completed filter, quotient Cauchy name, selected representative, countable-choice schedule, trichotomy decision, host real equality, or ambient completeness proof is refused by the carrier and by the local $\NameCert_{\LocatedCauchyFilterBasisUp}$ obligations.
\end{theorem}
\begin{proof}
Inspect the carrier rows of \autoref{def:cauchy-filter-basis-real-carrier}. They include only finite BHist data, hsame transport, Cont replay, dyadic tolerance ledgers, StreamName windows, RegSeqRat readbacks, the located basis witness, the LocatedCauchyFilter tail route, and the Real seal boundary.

The obligation surface of \autoref{thm:cauchy-filter-basis-real-obligations} is exhaustive. Every accepted consumer must pass through those listed rows, and no obligation names a hidden completed filter, quotient stream, selected representative, choice schedule, trichotomy decision, host equality, or completeness proof.

The tail and seal theorems keep the downstream routes ordered. Since $T$ and $E$ are reached only after the finite located basis witness is replayed, the packet has no escape path around its displayed finite data.
\end{proof}

\begin{closurestatus}{\LocatedCauchyFilterBasisUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-filter-basis-real-carrier}, \autoref{thm:cauchy-filter-basis-real-obligations}, \autoref{thm:cauchy-filter-basis-real-tail-refinement}, \autoref{thm:cauchy-filter-basis-real-seal-handoff}, and \autoref{thm:cauchy-filter-basis-real-nonescape} seed the located finite-basis interface between CauchyFilterBasis, LocatedCauchyFilter, StreamName, RegSeqRat, DyadicRatCore, and Real consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim completed filters, quotient Cauchy names, selected representatives, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Lean closure requires carrier admission, the located basis obligation surface, tail refinement, Real seal handoff, and nonescape for BEDC.Derived.LocatedCauchyFilterBasisUp.}
  \constructivestory{The construction starts from a CauchyFilterBasis row, reads a located dyadic request through StreamName windows, RegSeqRat readbacks, and DyadicRatCore ledgers, packages the finite witness as a LocatedCauchyFilter tail route, and treats Real access only as downstream seal provenance.}
\end{closurestatus}
