\chapter{A Concrete Naming Certificate for $\RealCompletionWindowFunctorUp$}
\label{ch:concrete-instances-real-completion-window-functor-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and Mac Lane on functoriality, the $\RealCompletionWindowFunctorUp$ packet records the finite BEDC surface where a displayed real-completion request is read functorially through bounded windows rather than through a quotient completion object. It sits over the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, and the completion-map discipline of \autoref{ch:concrete-instances-cauchy-completion-functoriality-namecert}. The packet gives downstream completion consumers one named window-functor route before any quotient stream, selected limit, host real equality, countable choice, or ambient $\RealUp$ completeness principle is available.

\begin{definition}[RealCompletionWindowFunctor carrier]
\label{def:real-completion-window-functor-carrier}
A $\RealCompletionWindowFunctorUp$ carrier is a finite $\BHist$ packet
$$
Q=(W,D,R,E,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the finite $\StreamNameUp$ window row naming the source and target observation windows used by the completion request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger comparing the source and target windows at the requested precision.
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows and tolerances.
\item $E$ is the terminal $\RealUp$ seal row reached only after $W,D,R$ have all been displayed.
\item $F$ is the functorial map row, read through $\CauchyCompletionFunctorialityUp$, recording how the displayed source window is transported to the displayed target window.
\item $H$ records componentwise $\hsame$ transport for $W,D,R,E,F,C,P,N$.
\item $C$ records displayed $\Cont$ replay from a completion-window request through $W,D,R,E,F,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RealCompletionWindowFunctorUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyCompletionFunctorialityUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealCompletionWindowFunctorUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through the nine displayed rows. It has no coordinate for quotient completion classes, selected representatives, host real equality, countable-choice schedules, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[RealCompletionWindowFunctor NameCert obligations]
\label{thm:real-completion-window-functor-namecert-obligations}
For every accepted $\RealCompletionWindowFunctorUp$ carrier
$$
Q=(W,D,R,E,F,H,C,P,N),
$$
the local $\NameCert_{\RealCompletionWindowFunctorUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item carrier admission for the displayed finite packet $Q$;
\item analytic readback order $W \longmapsto D \longmapsto R \longmapsto E$;
\item functorial map exposure through the row $F$ over the same windows and tolerances;
\item structural stability through $\hsame$ transport and displayed $\Cont$ replay;
\item provenance and local naming through $P$ and $N$.
\end{enumerate}
No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:real-completion-window-functor-carrier}. The accepted packet displays exactly $W,D,R,E,F,H,C,P,N$, so every local NameCert read must be a read of one of those coordinates.

The analytic route is ordered by the displayed rows. The finite StreamName windows $W$ are inspected before the dyadic tolerance ledger $D$, the regular rational readback $R$, and the terminal Real seal $E$.

The functorial row $F$ is attached to the same window and tolerance ledger through $\CauchyCompletionFunctorialityUp$. Thus a completion consumer receives only the displayed map action on the finite route, not a quotient completion map or a selected representative.

Finally the rows $H,C,P,N$ transport, replay, source, and name the same packet. Since no excluded object occurs as a carrier coordinate, no additional local obligation is available.
\end{proof}

\begin{theorem}[RealCompletionWindowFunctor finite route]
\label{thm:real-completion-window-functor-finite-route}
Every completion-facing read exported by an accepted $\RealCompletionWindowFunctorUp$ carrier factors through the finite route
$$
W \longmapsto D \longmapsto R \longmapsto E \longmapsto F \longmapsto H,C,P,N .
$$
Consequently the functorial completion-map row is consumed only after the StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat readback, and Real seal boundary have been displayed inside the same packet.
\end{theorem}
\begin{proof}
Apply \autoref{thm:real-completion-window-functor-namecert-obligations}. Its obligation surface exposes exactly carrier admission, analytic readback order, functorial map exposure, structural stability, provenance, and local naming.

Read the analytic side first. The rows $W,D,R,E$ display the finite observation windows, dyadic tolerance ledger, regular rational readback, and terminal Real seal.

Then read the functorial side through $F$ and the structural rows. The rows $H,C,P,N$ keep that map action attached to the same finite packet. Therefore the completion consumer cannot detach the functorial map from the displayed window route.
\end{proof}

\closureat{RealCompletionWindowFunctorUp}{seedStr}

\begin{closurestatus}{\RealCompletionWindowFunctorUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-completion-window-functor-carrier}, \autoref{thm:real-completion-window-functor-namecert-obligations}, and \autoref{thm:real-completion-window-functor-finite-route} seed the finite completion-window functor route over StreamName, DyadicRatCore, RegSeqRat, Real, CauchyCompletionFunctoriality, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected limits, host real equality, countable choice, ambient $\RealUp$ completeness, full functor laws for all completion objects, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-window order, tolerance readback, Real-seal routing, functorial-map exposure, transport, replay, provenance, and local naming for BEDC.Derived.RealCompletionWindowFunctorUp.}
  \constructivestory{A $\RealCompletionWindowFunctorUp$ packet is generated from StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a terminal Real seal, a CauchyCompletionFunctoriality map row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
