\chapter{A Concrete Naming Certificate for $\DomainTruthCertificateUp$}
\label{ch:concrete-instances-domain-truth-certificate-namecert}
\origin{ai}

The $\DomainTruthCertificateUp$ packet realizes the domain-indexed truth surface of \autoref{sec:truth-without-finality} as a finite BEDC NameCert carrier. It sits beside certified physical truth from \autoref{ch:concrete-instances-certified-physical-truth-namecert}, open fit from \autoref{ch:concrete-instances-reality-constrained-open-fit-namecert}, synthesis sealing from \autoref{ch:concrete-instances-realityconstrainedsynthesisseal-namecert}, final-synthesis ledgering from \autoref{ch:concrete-instances-reality-constrained-final-synthesis-ledger-namecert}, and failure-surface exposure from \autoref{ch:concrete-instances-realityconstrainedfailuresurface-namecert}. Those siblings supply fit, open continuation, seal, ledger, and defeat surfaces; this packet binds the displayed domain row before any truth export is accepted.

\begin{definition}[DomainTruthCertificate carrier]
\label{def:domain-truth-certificate-carrier}
A $\DomainTruthCertificateUp$ carrier is a finite $\BHist$ packet
$$
D=(T,U,B,A,C,O,F,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the certified truth row naming the local claim, source traces, and reality-facing signature admitted by the packet.
\item $U$ is the domain row recording the observation bundle, approximation tower, continuation class, and observer configuration over which the claim is read.
\item $B$ is the open-fit row recording the finite fit comparison and the boundary at which the domain remains open.
\item $A$ is the observer-invariance row recording the anchor or observer transport under which the claim remains publicly readable.
\item $C$ is the continuation row recording the permitted reuse and replay route inside the displayed domain.
\item $O$ is the failure-surface row naming domain exits, classifier mismatches, finite defeats, and later observations that can stop the export.
\item $F$ is the transport row recording componentwise $\hsame$ preservation for the truth, domain, open-fit, invariance, continuation, failure, replay, provenance, and local-name rows.
\item $H$ is the displayed $\Cont$ replay row through the same finite packet.
\item $R$ is the provenance row recording source, tower, classifier, ledger, sibling-certificate, and construction references.
\item $P$ is the package row over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the cited sibling packets.
\item $N$ is the local $\NameCert_{\DomainTruthCertificateUp}$ row binding the displayed domain-indexed truth packet.
\end{enumerate}
The carrier has no coordinate for final truth, model--reality identity, host truth, unbounded observation, hidden observer privilege, or truth export outside the displayed domain row.
\end{definition}
\leanchecked{BEDC.Derived.DomainTruthCertificateUp.DomainTruthCertificateTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DomainTruthCertificate NameCert obligations]
\label{thm:domain-truth-certificate-obligations}
For the carrier of \autoref{def:domain-truth-certificate-carrier}, the local $\NameCert_{\DomainTruthCertificateUp}$ surface consists exactly of carrier admission, domain-scope display, open-fit display, observer-invariance display, failure-surface display, componentwise transport, displayed replay, provenance, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier $D=(T,U,B,A,C,O,F,H,R,P,N)$. The rows $T,U,B,A,C,O$ expose the certified truth claim, the domain scope, the open-fit boundary, the observer-invariant route, the continuation replay scope, and the failure surface.

Read the structural rows. Transport through $F$ preserves each displayed component, replay through $H$ keeps the consumer inside the same finite route, provenance through $R$ records the source and sibling dependencies, and $P,N$ package and locally name the certificate.

Since no additional coordinate is available in the carrier, these rows exhaust the local NameCert surface. A domain-truth export that omits one row is only a projection, not an accepted $\DomainTruthCertificateUp$ packet.
\end{proof}

\begin{theorem}[DomainTruthCertificate non-escape]
\label{thm:domain-truth-certificate-nonescape}
An accepted $\DomainTruthCertificateUp$ packet excludes final truth, model--reality identity, host truth, unbounded observation, and domain leakage. Any export that asserts validity outside the displayed domain row $U$, or reads truth from a coordinate absent from
$$
T,U,B,A,C,O,F,H,R,P,N
$$
is rejected by the local $\NameCert_{\DomainTruthCertificateUp}$ surface.
\end{theorem}
\leanchecked{BEDC.Derived.DomainTruthCertificateUp.DomainTruthCertificateUp\_nonescape}
\begin{proof}
Use the carrier of \autoref{def:domain-truth-certificate-carrier}. The truth row $T$ is always read together with the domain row $U$, the open-fit row $B$, the observer-invariance row $A$, the continuation row $C$, and the failure row $O$.

The structural rows cannot widen the domain. Transport through $F$ preserves displayed components, replay through $H$ consumes the same route, provenance through $R$ records sources already named in the packet, and $P,N$ package and name the same finite certificate.

Thus final truth, model--reality identity, host truth, unbounded observation, and domain leakage would require a coordinate not present in the packet. The accepted route certifies domain truth only within the displayed finite surface.
\end{proof}

\begin{theorem}[DomainTruthCertificate sibling independence]
\label{thm:domain-truth-certificate-independence}
The $\DomainTruthCertificateUp$ packet is not bijective to $\CertifiedPhysicalTruthUp$, $\RealityConstrainedOpenFitUp$, $\RealityConstrainedSynthesisSealUp$, $\RealityConstrainedFinalSynthesisLedgerUp$, or $\RealityConstrainedFailureSurfaceUp$. Each sibling supplies a required surface, but none alone carries the displayed domain row tying truth, continuation, observer, failure, transport, replay, provenance, package, and local naming into one finite certificate.
\end{theorem}
\begin{proof}
Compare the displayed carrier with the sibling roles. $\CertifiedPhysicalTruthUp$ supplies the certified truth read, $\RealityConstrainedOpenFitUp$ supplies finite open fit, $\RealityConstrainedSynthesisSealUp$ supplies the synthesis seal, $\RealityConstrainedFinalSynthesisLedgerUp$ supplies ledger discipline, and $\RealityConstrainedFailureSurfaceUp$ supplies the defeat surface.

The row $U$ is the separating coordinate. It binds the observation bundle, approximation tower, continuation class, and observer configuration as the domain of the truth read, and the rows $C,F,H,R,P,N$ replay, transport, source, package, and name that same domain-indexed packet.

Therefore no listed sibling is bijective to $\DomainTruthCertificateUp$. Removing the domain row erases the certificate's scope, while replacing any sibling with the domain packet erases the sibling's specialized surface.
\end{proof}

\falsifiablePrediction{A domain-truth export that omits the domain row or asserts final validity over all future observations is not accepted by the local NameCert.}

\independenceWitness{certifiedphysicaltruth, realityconstrainedopenfit, realityconstrainedsynthesisseal, realityconstrainedfinalsynthesisledger, realityconstrainedfailuresurface: no sibling is bijective because DomainTruthCertificateUp adds the displayed certified-domain row tying truth, continuation, observer, failure, transport, replay, provenance, and local naming into one carrier.}

Lean follow-up must provide \texttt{Nontrivial DomainTruthCertificateUp} and \texttt{FieldFaithful DomainTruthCertificateUp} in \texttt{lean4/BEDC/Derived/DomainTruthCertificateUp/TasteGate.lean}.

\closureat{DomainTruthCertificateUp}{seedStr}

\begin{closurestatus}{\DomainTruthCertificateUp}
  \constructivestory{A $\DomainTruthCertificateUp$ packet is generated from a certified truth row, displayed domain row, open-fit row, observer-invariance row, continuation row, failure surface, componentwise transport, replay, provenance, package data, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:domain-truth-certificate-carrier}, \autoref{thm:domain-truth-certificate-obligations}, \autoref{thm:domain-truth-certificate-nonescape}, and \autoref{thm:domain-truth-certificate-independence} bind the finite domain-truth carrier, NameCert obligations, non-escape theorem, and sibling-independence theorem.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, final truth, model--reality identity, host truth, unbounded observation, or truth export outside the displayed domain row.}
  \upgradepath{Obligation closure requires checked carrier admission, domain-scope display, open-fit display, observer-invariance display, failure-surface display, transport, replay, provenance, local naming, TasteGate nontriviality, and field faithfulness for $T,U,B,A,C,O,F,H,R,P,N$.}
\end{closurestatus}
