\chapter{A Concrete Naming Certificate for $\BanachFixedPointStabilityUp$}
\label{ch:concrete-instances-banach-fixed-point-stability-namecert}
\origin{human}

Following Banach and Bishop--Bridges constructive metric analysis, the $\BanachFixedPointStabilityUp$ packet records the finite stability surface by which a displayed contraction orbit keeps its fixed-point seal attached to explicit Picard and Cauchy-modulus data. It sits after the fixed-point certificate of \autoref{ch:concrete-instances-banach-fixed-point-namecert}, the iteration ledger of \autoref{ch:concrete-instances-picard-iteration-namecert}, the contraction surface of \autoref{ch:concrete-instances-contractionmapping-namecert}, the complete-metric boundary of \autoref{ch:concrete-instances-completemetric-namecert}, the modulus schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a stability handoff for fixed-point consumers; it is not ambient real completeness, a selected host fixed point, a quotient orbit, a global contraction theorem, or a choice principle.

\begin{definition}[Banach fixed point stability carrier]
\label{def:banach-fixed-point-stability-carrier}
A $\BanachFixedPointStabilityUp$ carrier is a finite $\BHist$ packet
$$
B=(F,I,T,M,Q,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\BanachFixedPointUp$ source row naming the fixed-point certificate whose stability is being inspected.
\item $I$ is the $\PicardIterationUp$ orbit row, recording the finite prefix and tail schedule consumed by the stability packet.
\item $T$ is the $\ContractionMappingUp$ row that exposes the displayed contraction constant, comparison window, and contraction replay surface.
\item $M$ is the $\CompleteMetricUp$ dependency row, available only as the completion boundary used by the Picard orbit and not as ambient completeness for $\RealUp$.
\item $Q$ is the $\CauchyModulusUp$ stability schedule for the orbit tail and perturbation tolerance.
\item $R$ is the $\RegSeqRatUp$ readback row reached only after $I,T,M,Q$ have been displayed.
\item $E$ is the terminal $\RealUp$ seal row available only after the fixed-point source, Picard orbit, contraction row, completion boundary, modulus schedule, and regular-rational readback have been read.
\item $H$ records componentwise $\hsame$ transport for the displayed source, orbit, contraction, completion, modulus, readback, real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the fixed-point source through $F,I,T,M,Q,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BanachFixedPointStabilityUp$, $\BanachFixedPointUp$, $\PicardIterationUp$, $\ContractionMappingUp$, $\CompleteMetricUp$, $\CauchyModulusUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BanachFixedPointStabilityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,I,T,M,Q,R,E,H,C,P,N$. It has no coordinate for a selected host fixed point, quotient orbit equality, ambient $\RealUp$ completeness, global contraction soundness, trichotomy, or countable choice.
\end{definition}
\leanchecked{BEDC.Derived.BanachFixedPointStabilityUp.BanachFixedPointStabilityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Banach fixed point stability NameCert obligations]
\label{thm:banach-fixed-point-stability-namecert-obligations}
For every accepted $\BanachFixedPointStabilityUp$ carrier $B=(F,I,T,M,Q,R,E,H,C,P,N)$, the local $\NameCert_{\BanachFixedPointStabilityUp}$ surface consists exactly of carrier admission for the displayed fixed-point source $F$, Picard orbit $I$, contraction row $T$, complete-metric dependency $M$, Cauchy-modulus schedule $Q$, regular-rational readback $R$, terminal real seal $E$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:banach-fixed-point-stability-carrier}. The analytic rows visible to a stability consumer are exactly $F,I,T,M,Q,R,E$, followed by transport, replay, provenance, and naming.

The fixed-point source is not read alone. The Picard row $I$ and contraction row $T$ display the orbit and contraction comparison before the complete-metric dependency $M$ and modulus schedule $Q$ can be consumed.

The Real-facing endpoint is downstream from the same finite route. The regular-rational row $R$ is read only from the displayed orbit, contraction, completion, and modulus rows, and the terminal seal $E$ is read only after $R$.

Finally $H,C,P,N$ transport, replay, source, and name this packet. Since the carrier has no excluded coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Banach fixed point stability Picard-Cauchy handoff]
\label{thm:banach-fixed-point-stability-picard-cauchy-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\BanachFixedPointStabilityUp$ packet factors through the finite route
$$
\BanachFixedPointUp \longmapsto \PicardIterationUp \longmapsto \ContractionMappingUp \longmapsto \CompleteMetricUp \longmapsto \CauchyModulusUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
The handoff exposes only the displayed fixed-point source, Picard orbit, contraction comparison, complete-metric dependency, Cauchy-modulus schedule, regular-rational readback, terminal real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows. It exports no selected host fixed point, quotient orbit equality, hidden completion theorem, ambient $\RealUp$ completeness, global contraction soundness, trichotomy, or countable-choice schedule.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:banach-fixed-point-stability-namecert-obligations}. It places every stability read behind the fixed-point source, Picard orbit, contraction comparison, complete-metric dependency, and explicit modulus schedule.

Next open the handoff to regular-rational data. The rows $I,T,M,Q$ determine the displayed Cauchy tail route, so the $\RegSeqRatUp$ row $R$ is a finite readback from those rows rather than a quotient orbit or host-selected fixed point.

The terminal real seal is last. The $\RealUp$ row $E$ is consumed only after $R$ has been displayed, while $H,C,P,N$ preserve the same dependency order under transport, replay, provenance, and local naming.

Thus any $\RegSeqRatUp$ or $\RealUp$ consumer sees exactly the stated Picard-Cauchy route and cannot bypass it through an ambient completeness or choice object.
\end{proof}

\begin{theorem}[Banach fixed point stability modulus nonescape]
\label{thm:banach-fixed-point-stability-modulus-nonescape}
Let $B=(F,I,T,M,Q,R,E,H,C,P,N)$ be an accepted $\BanachFixedPointStabilityUp$ carrier. Every perturbation consumer and every tail-stability consumer of $B$ must read the $\CauchyModulusUp$ schedule $Q$ before it can read the regular-rational row $R$ or the terminal $\RealUp$ seal row $E$.

Consequently no such consumer can obtain a selected host fixed point, quotient orbit equality, hidden completion theorem, ambient $\RealUp$ completeness, global contraction soundness, trichotomy, or countable-choice schedule from $R$ or $E$ without first exposing the displayed modulus row $Q$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:banach-fixed-point-stability-carrier}. The rows are ordered so that $Q$ is the displayed Cauchy-modulus schedule for the orbit tail and perturbation tolerance, while $R$ and $E$ are downstream readback and seal rows.

Apply \autoref{thm:banach-fixed-point-stability-namecert-obligations}. It says that the local NameCert surface contains the fixed-point source, Picard orbit, contraction row, complete-metric dependency, Cauchy-modulus schedule, regular-rational readback, and terminal real seal as listed carrier rows, with no excluded coordinate.

Next apply \autoref{thm:banach-fixed-point-stability-picard-cauchy-handoff}. The displayed route reaches $\RegSeqRatUp$ and $\RealUp$ only after $\CauchyModulusUp$, so a perturbation or tail-stability request that tries to read $R$ or $E$ has already passed through $Q$.

The refusal clauses follow because the carrier and handoff theorems export no selected host fixed point, quotient orbit equality, hidden completion theorem, ambient Real completeness, global contraction theorem, trichotomy, or countable-choice row. Thus $Q$ is a nonescape boundary for all tail-stability and perturbation reads.
\end{proof}

\closureat{BanachFixedPointStabilityUp}{seedStr}

\begin{closurestatus}{\BanachFixedPointStabilityUp}
  \constructivestory{A $\BanachFixedPointStabilityUp$ packet is generated from a BanachFixedPoint source row, PicardIteration orbit, ContractionMapping comparison, CompleteMetric dependency, CauchyModulus schedule, RegSeqRat readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:banach-fixed-point-stability-carrier}, \autoref{thm:banach-fixed-point-stability-namecert-obligations}, and \autoref{thm:banach-fixed-point-stability-picard-cauchy-handoff} seed the finite stability handoff from Banach fixed-point data through Picard, contraction, completion, modulus, regular-rational, and real-seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected host fixed points, quotient orbit equality, hidden completion theorems, ambient RealUp completeness, global contraction soundness, trichotomy, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Picard orbit ordering, contraction comparison stability, complete-metric dependency confinement, Cauchy-modulus exactness, RegSeqRat handoff, RealUp seal confinement, transport stability, continuation replay, and provenance nonescape for BEDC.Derived.BanachFixedPointStabilityUp.}
\end{closurestatus}
