\chapter{A Concrete Naming Certificate for $\BoundedMetricSpaceUp$}
\label{ch:concrete-instances-bounded-metric-space-namecert}
\origin{human}

Following Hausdorff and Kelley metric-space practice, the $\BoundedMetricSpaceUp$ packet records the bounded metric-space interface as finite BEDC NameCert data. It sits between the metric carrier of \autoref{ch:concrete-instances-metric-space-namecert}, the center-radius containment row of \autoref{ch:concrete-instances-metricball-namecert}, the bounded-subset surface of \autoref{ch:concrete-instances-boundedset-namecert}, the diameter handoff of \autoref{ch:concrete-instances-metric-diameter-namecert}, the ordered-real bound route of \autoref{ch:concrete-instances-real-alg-order-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the completion-facing consumers of \autoref{ch:concrete-instances-completion-namecert} and \autoref{ch:concrete-instances-metriccompletion-namecert}. The packet supplies finite-net, Cauchy, compact-metric, and diameter consumers with a displayed bounded metric source without importing compactness, host suprema, selected centers, quotient equality, or ambient completeness.

\begin{definition}[BoundedMetricSpace carrier]
\label{def:bounded-metric-space-carrier}
A $\BoundedMetricSpaceUp$ carrier is a finite $\BHist$ packet
$$
Q=(X,B,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricSpaceUp$ carrier row. It supplies the point classifier, metric-source data, real-valued distance route, zero-distance classifier, symmetry row, and triangle row.
\item $B$ is the bounded-containment row. It records the $\MetricBallUp$ center-radius ledger together with the $\BoundedSetUp$ membership classifier that every admitted point must read before boundedness is exposed.
\item $D$ is the $\MetricDiameterUp$ row. It names the finite diameter-bound handoff consumed by diameter, finite-net, Cauchy, and compact-metric readers.
\item $R$ is the real-bound readback row. It routes the radius and diameter bounds through $\RealUp$ and the ordered comparison surface of $\RealAlgOrderUp$.
\item $H$ records componentwise $\hsame$ transport for the metric carrier, containment row, diameter row, real-bound readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a bounded-metric request through metric admission, bounded-set containment, metric-ball comparison, diameter-bound readback, ordered-real comparison, and completion-facing handoff.
\item $P$ is the $\Pkg$ provenance over $\BoundedMetricSpaceUp$, $\MetricSpaceUp$, $\MetricBallUp$, $\BoundedSetUp$, $\MetricDiameterUp$, $\RealUp$, $\RealAlgOrderUp$, $\CompletionUp$, $\MetricCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BoundedMetricSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,B,D,R,H,C,P,N$. It has no coordinate for a host subset, host supremum, selected bounding center, selected diameter witness, compactness theorem, quotient completion, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[BoundedMetricSpace NameCert obligations]
\label{thm:bounded-metric-space-namecert-obligations}
For every accepted $\BoundedMetricSpaceUp$ carrier $Q=(X,B,D,R,H,C,P,N)$, the local $\NameCert_{\BoundedMetricSpaceUp}$ surface consists exactly of the following obligation families:
\begin{enumerate}
\item metric-source admission for the displayed $\MetricSpaceUp$ row $X$;
\item bounded-containment admission for the $\MetricBallUp$ and $\BoundedSetUp$ rows stored in $B$;
\item diameter-bound admission for the $\MetricDiameterUp$ row $D$;
\item real-bound readback through $\RealUp$ and $\RealAlgOrderUp$ in $R$;
\item componentwise transport, displayed replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
Consequently a downstream finite-net, Cauchy, compact-metric, diameter, or completion-facing consumer may read bounded metric-space data only through the displayed metric, containment, diameter, ordered-real, and structural rows. The packet exports no host supremum, compactness theorem, selected bound, quotient completion, countable-choice selector, or ambient real completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bounded-metric-space-carrier}. The only analytic rows are the metric source $X$, the bounded-containment row $B$, the diameter row $D$, and the real-bound readback row $R$.

The containment side is read first. The row $B$ combines the center-radius ledger of \autoref{ch:concrete-instances-metricball-namecert} with the bounded-subset classifier of \autoref{ch:concrete-instances-boundedset-namecert}, so membership containment is visible before any bounded-space consumer receives the packet.

The diameter and real-bound rows are downstream from that containment. The row $D$ supplies the sibling handoff of \autoref{ch:concrete-instances-metric-diameter-namecert}, and $R$ records that the bound is read through $\RealUp$ and $\RealAlgOrderUp$ rather than through a host supremum.

Finally $H,C,P,N$ transport, replay, source, and name the same displayed rows. Since no excluded analytic object is a coordinate of $Q$, the listed obligation families exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[BoundedMetricSpace diameter-bound handoff]
\label{thm:bounded-metric-space-diameter-bound-handoff}
Every diameter, finite-net, Cauchy, compact-metric, or completion-facing read accepted from a $\BoundedMetricSpaceUp$ packet factors through the finite route
$$
\MetricSpaceUp
\longmapsto
\MetricBallUp,\BoundedSetUp
\longmapsto
\MetricDiameterUp
\longmapsto
\RealUp,\RealAlgOrderUp
\longmapsto
\CompletionUp,\MetricCompletionUp .
$$
The exported handoff is a displayed bounded metric source with containment and diameter-bound rows already visible. It does not provide compactness, a host supremum, a selected bounding center, a selected maximum pair, quotient completion equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from an accepted packet $Q=(X,B,D,R,H,C,P,N)$. A consumer first opens the metric row $X$, so every subsequent boundedness or diameter read remains attached to the same point classifier and distance route.

Read containment through $B$. This exposes the center-radius and bounded-subset rows before any finite-net or Cauchy consumer can treat the source as bounded.

Next read the diameter row $D$ and the ordered-real readback $R$. These rows hand the displayed bound to the sibling diameter packet and to the $\RealUp$ and $\RealAlgOrderUp$ comparison surfaces, with no host supremum or selected maximum pair.

The completion-facing route is only a consumer of that finite surface. The structural rows $H,C,P,N$ preserve the same path under transport and replay, so no quotient completion, choice schedule, or ambient completeness principle is exported.
\end{proof}

\closureat{BoundedMetricSpaceUp}{seedStr}

\begin{closurestatus}{\BoundedMetricSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bounded-metric-space-carrier}, \autoref{thm:bounded-metric-space-namecert-obligations}, and \autoref{thm:bounded-metric-space-diameter-bound-handoff} seed the finite bounded metric-space packet over metric, ball-containment, bounded-subset, diameter, ordered-real, and completion-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim compactness, host suprema, selected bounds, quotient completions, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure asks for checked metric admission, bounded-containment admission, diameter-bound handoff, real-bound readback, transport, replay, provenance, and local naming for BEDC.Derived.BoundedMetricSpaceUp.}
  \constructivestory{A $\BoundedMetricSpaceUp$ packet is generated from a MetricSpaceUp carrier, MetricBallUp and BoundedSetUp containment rows, a MetricDiameterUp bound row, RealUp and RealAlgOrderUp readback, completion-facing handoff data, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
