\chapter{A Concrete Naming Certificate for $\ReassignmentMassSubcubeUp$}
\label{ch:concrete-instances-reassignment-mass-subcube-namecert}
\origin{ai}

The $\ReassignmentMassSubcubeUp$ packet realizes the maximum-mass subcube geometry branch of the DNA six-bit boundary tile analysis as finite NameCert data. It reads the reassignment weight row, the subcube mass ledger, and the nested maximum-mass subcube theorem of \autoref{def:philosophy-reassignment-weight-subcube-mass} and \autoref{thm:philosophy-nested-maximum-mass-subcubes} through displayed codon-window and reassignment sibling packets. The packet consumes $\CodonSixBitWindowUp$, $\SixBoundaryTileCoverageUp$, $\ReassignmentSupportCompressionUp$, and $\AlternativeCodeReassignmentUp$ rows before any maximum-mass face can be named; it is not a biological mechanism claim, a host optimization oracle, or a hidden table-family search.

\begin{definition}[ReassignmentMassSubcube carrier]
\label{def:reassignment-mass-subcube-carrier}
A $\ReassignmentMassSubcubeUp$ carrier is a finite $\BHist$ packet
$$
M=(W,B,S,A,R,Q,L,N,H,C,P,K)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the $\CodonSixBitWindowUp$ source-window row exposing the six coordinate bits for codon subcube reads.
\item $B$ is the $\SixBoundaryTileCoverageUp$ boundary-coverage row used to keep boundary-trigger coverage visible while subcubes are inspected.
\item $S$ is the $\ReassignmentSupportCompressionUp$ support row, exposing the finite reassigned support and motif-cover surface.
\item $A$ is the $\AlternativeCodeReassignmentUp$ comparison-table row from which reassignment weights are read.
\item $R$ is the reassignment-weight row, recording each displayed codon weight $w(c)$ from the curated comparison surface.
\item $Q$ is the finite subcube ledger, listing the inspected axis-aligned $Q_5,Q_4,Q_3,Q_2$ faces and their fixed-coordinate conditions.
\item $L$ is the subcube-mass ledger, recording each displayed mass $M(S)$ as a finite sum over the visible weight row $R$.
\item $N$ is the nested maximum-mass row, recording the unique maximum-mass chain $Q_5\supset Q_4\supset Q_3\supset Q_2$ displayed by the source theorem.
\item $H$ records componentwise $\hsame$ transport for source-window, boundary-coverage, support-compression, alternative-code, weight, subcube, mass, nested-chain, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from reassignment comparison to weights, from weights to finite subcube masses, and from masses to the nested maximum-mass row.
\item $P$ is the $\Pkg$ provenance over $\ReassignmentMassSubcubeUp$, $\CodonSixBitWindowUp$, $\SixBoundaryTileCoverageUp$, $\ReassignmentSupportCompressionUp$, $\AlternativeCodeReassignmentUp$, the source reassignment-mass geometry vision, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $K$ is the local $\NameCert_{\ReassignmentMassSubcubeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these twelve rows. It has no coordinate for uncurated code tables, stochastic evolutionary dynamics, biochemical causality, a host argmax operator, quotient codon equality, or hidden biological semantics.
\end{definition}

\begin{theorem}[ReassignmentMassSubcube NameCert obligations]
\label{thm:reassignment-mass-subcube-namecert-obligations}
For every accepted $\ReassignmentMassSubcubeUp$ carrier $M=(W,B,S,A,R,Q,L,N,H,C,P,K)$, the local $\NameCert_{\ReassignmentMassSubcubeUp}$ surface consists exactly of carrier admission for the displayed codon window, boundary coverage, support compression, alternative-code comparison, reassignment-weight, finite subcube, mass, nested maximum-mass, transport, replay, provenance, and local naming rows. The mass row must compute only finite sums over the displayed weight row, and the nested row must expose the unique maximum-mass chain only after $W,B,S,A,R,Q,L$ are visible.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:reassignment-mass-subcube-carrier}. The first four rows provide the source coordinate, boundary coverage, reassignment support, and alternative-table comparison surfaces.

The weight row $R$ is then a finite comparison read from $A$, and the subcube ledger $Q$ lists the inspected axis-aligned faces over the six-bit source window $W$. The mass ledger $L$ can therefore compute only finite sums of displayed weights.

The nested maximum-mass row $N$ is downstream of those finite sums. It records the displayed chain from the vision theorem rather than invoking a host optimization oracle.

Finally $H,C,P,K$ transport, replay, source, and name the same packet. Since no uncurated table family, stochastic dynamics, biochemical mechanism, host argmax, quotient codon equality, or hidden biological semantics occurs in the carrier, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[ReassignmentMassSubcube sibling route]
\label{thm:reassignment-mass-subcube-sibling-route}
Every accepted $\ReassignmentMassSubcubeUp$ read factors through
$$
\CodonSixBitWindowUp,\SixBoundaryTileCoverageUp,\ReassignmentSupportCompressionUp,\AlternativeCodeReassignmentUp
\longmapsto
R,Q,L,N
\longmapsto
H,C,P,K .
$$
Thus a maximum-mass subcube claim is read as finite reassignment geometry over displayed codon coordinates, boundary-tile coverage, support compression, and alternative-code comparison rows. It cannot be consumed as a free-standing biological mechanism, host optimization theorem, unbounded genetic-code survey, or quotient of codon labels.
\end{theorem}
\begin{proof}
Begin with the sibling sources. The codon six-bit window supplies the coordinate carrier, the six-boundary tile coverage row keeps trigger support visible, the reassignment-support-compression row exposes the finite support surface, and the alternative-code-reassignment row supplies the comparison table data.

Only after those sources are displayed can the packet read reassignment weights and subcube masses. The rows $R,Q,L$ bind the finite weights, inspected faces, and mass sums, while $N$ records the nested maximum-mass chain.

The structural rows then preserve that route. Transport, replay, provenance, and local naming cannot add the excluded biological or host-optimization coordinates, so every accepted read remains inside the displayed sibling lattice.
\end{proof}

\falsifiablePrediction{An accepted $\ReassignmentMassSubcubeUp$ read is refuted if the finite maximum-mass subcube route can bypass reassignment-support-compression, alternative-code-reassignment, codon-six-bit-window, or six-boundary-tile-coverage rows.}

\independenceWitness{reassignment-support-compression, alternative-code-reassignment, codon-six-bit-window, six-boundary-tile-coverage: no listed sibling is bijective with $\ReassignmentMassSubcubeUp$ because the siblings respectively expose support compression, comparison-table reassignment, coordinate windows, or trigger coverage, while this packet jointly binds reassignment weights, subcube ledgers, finite mass sums, nested maximum-mass exposure, transport, replay, provenance, and local naming.}

The Lean $\mathsf{TasteGate.lean}$ development for $\ReassignmentMassSubcubeUp$ must include explicit $\Nontrivial\ \ReassignmentMassSubcubeUp$ and $\FieldFaithful\ \ReassignmentMassSubcubeUp$ instances preserving $W,B,S,A,R,Q,L,N,H,C,P,K$ as separate displayed fields.

\closureat{ReassignmentMassSubcubeUp}{seedStr}

\begin{closurestatus}{\ReassignmentMassSubcubeUp}
  \constructivestory{A $\ReassignmentMassSubcubeUp$ packet is generated from codon six-bit windows, six-boundary tile coverage rows, reassignment-support compression rows, alternative-code comparison rows, reassignment weights, finite subcube ledgers, mass sums, nested maximum-mass rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:reassignment-mass-subcube-carrier}, \autoref{thm:reassignment-mass-subcube-namecert-obligations}, and \autoref{thm:reassignment-mass-subcube-sibling-route} seed the finite maximum-mass subcube NameCert surface for reassignment geometry.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological mechanism, uncurated genetic-code surveys, stochastic evolutionary dynamics, host optimization, quotient codon equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, sibling-source exposure, reassignment-weight exactness, finite subcube ledger exposure, mass-sum exactness, nested maximum-mass routing, Nontrivial ReassignmentMassSubcubeUp, and FieldFaithful ReassignmentMassSubcubeUp for BEDC.Derived.ReassignmentMassSubcubeUp.}
\end{closurestatus}
