\chapter{A Concrete Naming Certificate for $\RealTriangleInequalityUp$}
\label{ch:concrete-instances-real-triangle-inequality-namecert}
\origin{human}

Following Bishop and Bridges' constructive treatment of metric real names, the $\RealTriangleInequalityUp$ packet records the finite three-leg route by which a displayed real distance estimate is assembled without importing quotient real equality or an ambient completeness theorem. It sits beside the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the stream-window discipline of \autoref{ch:concrete-instances-streamname-namecert}.

\begin{definition}[Real triangle inequality carrier]
\label{def:real-triangle-inequality-carrier}
A $\RealTriangleInequalityUp$ carrier is a finite $\BHist$ packet
$$
T=(A,B,M,D,W,H,C,P,N)
$$
with the following displayed coordinates:
\begin{enumerate}
\item $A$ and $B$ are the two endpoint $\RealUp$ equality rows whose distance comparison is being bounded.
\item $M$ is the intermediate $\RegSeqRatUp$ row that supplies the middle leg of the finite rational comparison.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger carrying the three displayed radii and the exact middle-leg budget.
\item $W$ is the $\StreamNameUp$ window family through which the two endpoints and the intermediate row are inspected.
\item $H$ stores componentwise $\hsame$ transport for endpoint rows, the middle readback row, dyadic budgets, windows, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a consumer request through $A,B,M,D,W,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RealTriangleInequalityUp$, $\RealUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RealTriangleInequalityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these finite coordinates. It has no coordinate for host real equality, quotient streams, selected limits, trichotomy, or ambient completeness.
\end{definition}

\begin{theorem}[Real triangle inequality NameCert obligations]
\label{thm:real-triangle-inequality-namecert}
For an accepted $\RealTriangleInequalityUp$ carrier $T=(A,B,M,D,W,H,C,P,N)$, the local $\NameCert_{\RealTriangleInequalityUp}$ surface consists exactly of endpoint admission through the two displayed $\RealUp$ equality rows $A,B$, dyadic middle-leg exactness through the ledger $D$, $\RegSeqRatUp$ replay through $M$, $\StreamNameUp$ window inspection through $W$, terminal $\RealUp$ seal handoff for the three-leg comparison, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row $N$. No consumer can escape from this surface to host real equality, quotient streams, selected limits, trichotomy, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-triangle-inequality-carrier}. The two endpoint rows $A,B$, the intermediate readback row $M$, the dyadic ledger $D$, the stream windows $W$, transport, replay, provenance, and naming row are all displayed coordinates of the finite packet.

Endpoint admission is therefore read only through $A$ and $B$. The middle leg is read through $M$, while $D$ records the exact dyadic budget that joins the two endpoint comparisons through the displayed intermediate row.

Replay the consumer request through $C$ after transporting coordinates with $H$. The replay order exposes the $\StreamNameUp$ windows, the $\RegSeqRatUp$ middle row, and the $\DyadicRatCoreUp$ ledger before any terminal $\RealUp$ seal is inspected.

The exclusions are the carrier inventory. Since no coordinate stores host real equality, a quotient stream object, a selected limit, trichotomy data, or an ambient completeness theorem, the local naming certificate cannot export any of them.
\end{proof}

\closureat{RealTriangleInequalityUp}{seedStr}

\begin{closurestatus}{\RealTriangleInequalityUp}
  \constructivestory{A $\RealTriangleInequalityUp$ packet is generated from two endpoint $\RealUp$ equality rows, one intermediate $\RegSeqRatUp$ row, a $\DyadicRatCoreUp$ tolerance ledger, finite $\StreamNameUp$ windows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-triangle-inequality-carrier} and \autoref{thm:real-triangle-inequality-namecert} seed the finite three-leg real route over RealUp, RegSeqRatUp, DyadicRatCoreUp, StreamNameUp, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real equality, quotient stream equality, selected limits, trichotomy, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked endpoint admission, dyadic middle-leg exactness, RegSeqRat replay, RealUp seal handoff, and non-escape for BEDC.Derived.RealTriangleInequalityUp.}
\end{closurestatus}
