\chapter{A Concrete Naming Certificate for $\DarbouxCriterionUp$}
\label{ch:concrete-instances-darboux-criterion-namecert}
\origin{human}

Following Darboux, Riemann, and Bishop--Bridges constructive integration, the $\DarbouxCriterionUp$ packet records the upper-lower gap test as finite NameCert evidence. It sits between the lower and upper Darboux sum packets of \autoref{ch:concrete-instances-lower-darboux-sum-namecert} and \autoref{ch:concrete-instances-upper-darboux-sum-namecert}, the Darboux-sum surface of \autoref{ch:concrete-instances-darboux-sum-namecert}, and the Riemann-facing consumers of \autoref{ch:concrete-instances-riemann-integrable-namecert} and \autoref{ch:concrete-instances-riemannintegral-namecert}. The packet exposes a displayed partition, lower sum, upper sum, gap, tolerance, regular rational readback, and real seal; it does not import host suprema, measure completion, a selected mesh, or ambient $\RealUp$ completeness.

\begin{definition}[Darboux criterion carrier]
\label{def:darboux-criterion-carrier}
A $\DarbouxCriterionUp$ carrier is a finite $\BHist$ packet
$$
K=(P,L,U,G,T,R,E,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the finite partition row, recording the inspected interval endpoints and refinement requests.
\item $L$ is the $\LowerDarbouxSumUp$ row attached to $P$.
\item $U$ is the $\UpperDarbouxSumUp$ row attached to the same partition row $P$.
\item $G$ is the upper-minus-lower gap row comparing $U$ and $L$ inside the displayed rational ledger.
\item $T$ is the tolerance row, recording the positive rational request against which $G$ is checked.
\item $R$ is the $\RegSeqRatUp$ readback row reached from the same finite partition and gap evidence.
\item $E$ is the terminal $\RealUp$ seal row, exposed only after $P,L,U,G,T,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for partition, lower-sum, upper-sum, gap, tolerance, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tolerance request through $P,L,U,G,T,R,E$.
\item $Q$ is the $\Pkg$ provenance over $\DarbouxCriterionUp$, $\DarbouxSumUp$, $\LowerDarbouxSumUp$, $\UpperDarbouxSumUp$, $\RiemannIntegrableUp$, $\RiemannIntegralUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DarbouxCriterionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for host suprema or infima, measure completion, a selected mesh, an ambient completeness principle, a quotient real, or a global integration theorem.
\end{definition}

\begin{theorem}[Darboux criterion NameCert obligations]
\label{thm:darboux-criterion-namecert-obligations}
For every accepted $\DarbouxCriterionUp$ carrier
$$
K=(P,L,U,G,T,R,E,H,C,Q,N),
$$
the local $\NameCert_{\DarbouxCriterionUp}$ surface consists exactly of carrier admission for the displayed rows, partition exposure, lower-sum and upper-sum compatibility over the same partition, gap comparison against the tolerance row, regular rational readback, terminal real-seal routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No obligation is stored outside $P,L,U,G,T,R,E,H,C,Q,N$.
\end{theorem}
\begin{proof}
Project the carrier. The accepted packet exposes the partition row $P$, the paired lower and upper Darboux sum rows $L,U$, the gap row $G$, the tolerance row $T$, the regular readback row $R$, the seal row $E$, and the structural rows $H,C,Q,N$.

The lower and upper sum rows are tied to the same partition row, so a gap comparison cannot switch partitions while the criterion is being read. The tolerance row fixes the request against which the displayed gap is checked.

The regular readback and real seal are downstream of those finite rows. Componentwise transport and replay preserve the same order, while provenance and naming record the listed sibling packets.

Since host suprema, measure completion, selected meshes, quotient reals, ambient completeness, and global integration theorems are absent from the carrier coordinates, the displayed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Darboux criterion upper-lower gap route]
\label{thm:darboux-criterion-upper-lower-gap-route}
Every $\RiemannIntegrableUp$, $\RiemannIntegralUp$, or regulated-integral-facing read of an accepted $\DarbouxCriterionUp$ packet factors through the finite route
$$
P,L,U \longmapsto G,T \longmapsto R \longmapsto E .
$$
Thus the consumer first reads a displayed partition, lower Darboux sum, and upper Darboux sum; then it reads the upper-minus-lower gap and tolerance rows; then it reads the $\RegSeqRatUp$ handoff and terminal $\RealUp$ seal. The packet exports no direct route through host suprema, measure completion, selected mesh choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:darboux-criterion-namecert-obligations}. They require carrier admission and classifier transport through the displayed rows of \autoref{def:darboux-criterion-carrier}.

The partition row $P$ is read before either sum row can be used. The rows $L$ and $U$ are therefore paired over the same finite partition, and $G$ is the displayed comparison between those paired rows.

The tolerance row $T$ is the only request against which the gap is consumed. After that finite comparison has been displayed, the read may pass to $R$ and then to the real seal row $E$.

The excluded routes are not coordinates of the carrier. Hence every integration-facing consumer receives the upper-lower gap criterion only through the finite partition, sum, gap, tolerance, regular-readback, and seal route.
\end{proof}

\closureat{DarbouxCriterionUp}{seedStr}

\begin{closurestatus}{\DarbouxCriterionUp}
  \constructivestory{A $\DarbouxCriterionUp$ packet is generated from a displayed partition, lower and upper Darboux sum rows, an upper-minus-lower gap row, a tolerance row, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:darboux-criterion-carrier}, \autoref{thm:darboux-criterion-namecert-obligations}, and \autoref{thm:darboux-criterion-upper-lower-gap-route} seed the finite upper-lower gap criterion for Riemann-facing and regulated-integral-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host suprema, measure completion, selected mesh choice, quotient real equality, ambient Real completeness, Lean verification, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, partition exposure, paired lower and upper sum compatibility, gap tolerance comparison, regular readback, real-seal routing, transport, replay, provenance, and local naming for BEDC.Derived.DarbouxCriterionUp.}
\end{closurestatus}
