\chapter{A Concrete Naming Certificate for $\CauchyInterlacingUp$}
\label{ch:concrete-instances-cauchy-interlacing-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\CauchyInterlacingUp$ packet records the finite interlacing route by which two regular rational names are merged into one Real-facing seal. It sits over the finite StreamName schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the tail-equivalence handoff of \autoref{ch:concrete-instances-cauchy-tail-equivalence-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the even/odd merge as displayed certificate data; it is not a quotient stream, selected limit, countable-choice schedule, or ambient completeness principle.

\begin{definition}[Cauchy interlacing carrier]
\label{def:cauchy-interlacing-carrier}
A $\CauchyInterlacingUp$ carrier is a finite $\BHist$ packet
$$
K=(A,B,W,D,T,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the two $\RegSeqRatUp$ source rows whose regular tails are to be merged.
\item $W$ is the even/odd $\StreamNameUp$ schedule row. Even windows read $A$, odd windows read $B$, and the row records the finite requests needed by the merged consumer.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger for the two source tails and the interlaced tail.
\item $T$ is the $\CauchyTailEquivalenceUp$ handoff row witnessing that the even and odd tails feed the same regular Cauchy boundary.
\item $R$ is the terminal $\RealUp$ seal row reached only after $A,B,W,D,T$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the two source rows, schedule, tolerance ledger, tail-equivalence handoff, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the finite route
$$
A,B,W,D,T \longmapsto R .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyInterlacingUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\CauchyTailEquivalenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyInterlacingUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these rows. Its classifier compares accepted packets only through $A,B,W,D,T,R,H,C,P,N$ and has no coordinate for quotient stream equality, selected representatives, countable choice, host limits, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy interlacing NameCert obligations]
\label{thm:cauchy-interlacing-namecert-obligations}
For every accepted $\CauchyInterlacingUp$ carrier
$$
K=(A,B,W,D,T,R,H,C,P,N),
$$
the local $\NameCert_{\CauchyInterlacingUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the two $\RegSeqRatUp$ sources, even/odd $\StreamNameUp$ schedule, dyadic tolerance ledger, tail-equivalence handoff, Real seal, transport, replay, provenance, and local naming row;
\item schedule discipline, requiring every merged read to identify whether it is reading the even source row $A$ or the odd source row $B$ through $W$;
\item dyadic tolerance exactness, requiring $D$ to record the source-tail and merged-tail tolerances consumed by the interlacing route;
\item tail handoff stability, requiring $T$ to mediate the passage from the two regular tails to one common Cauchy boundary before $R$ is visible;
\item real-seal nonescape, requiring $R$ to remain downstream of $A,B,W,D,T$;
\item componentwise transport, displayed replay, package provenance, and local naming stability through $H,C,P,N$;
\item ledger refusal, excluding quotient streams, selected limits, countable choice, host sequence limits, trichotomy, and ambient $\RealUp$ completeness.
\end{enumerate}
No Cauchy interlacing obligation is stored outside these rows.
\end{theorem}

\begin{proof}
Project the accepted carrier $K=(A,B,W,D,T,R,H,C,P,N)$. The visible coordinates are exactly the two regular rational source rows, one finite even/odd schedule, one dyadic tolerance ledger, one tail-equivalence handoff, one Real seal row, and the structural rows.

The schedule row $W$ fixes the finite interlacing order. Even requests read $A$ and odd requests read $B$, so no merged consumer can inspect an unrecorded source position.

The dyadic ledger $D$ and tail-equivalence row $T$ then bind the two regular tails to one Cauchy boundary. The Real seal $R$ is downstream of that route, while $H,C,P,N$ transport, replay, source, and name the same displayed rows.

Since the excluded host objects have no carrier coordinate, replay edge, provenance entry, or local naming row, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy interlacing RegSeqRat handoff]
\label{thm:cauchy-interlacing-regseqrat-handoff}
Every accepted $\CauchyInterlacingUp$ carrier exposes the merged regular rational read only through the finite route
$$
A,B,W,D,T \longmapsto R \longmapsto H,C,P,N .
$$
Thus a consumer receives the two $\RegSeqRatUp$ source rows, the even/odd $\StreamNameUp$ schedule, the $\DyadicRatCoreUp$ tolerance ledger, the $\CauchyTailEquivalenceUp$ handoff, the terminal $\RealUp$ seal row, componentwise transport, continuation replay, provenance, and local naming before it can use the merged real-facing name.
\end{theorem}

\begin{proof}
Start with the carrier projection. The two source rows $A$ and $B$ are independent displayed $\RegSeqRatUp$ inputs, and the only row that relates them to one merged stream is the even/odd schedule $W$.

Read the dyadic ledger and tail handoff. The row $D$ supplies the tolerances for both source tails and for the interlaced tail, while $T$ records the CauchyTailEquivalence passage from those two tails to one common boundary.

Only after $A,B,W,D,T$ have been displayed can $R$ be read as the Real-facing seal. The structural rows $H,C,P,N$ preserve the same dependency order, so the merged regular rational handoff cannot bypass the displayed schedule or tolerance ledger.
\end{proof}

\begin{theorem}[Cauchy interlacing Real seal nonescape]
\label{thm:cauchy-interlacing-real-seal-nonescape}
An accepted $\CauchyInterlacingUp$ consumer that reaches the terminal $\RealUp$ seal must have already displayed the two $\RegSeqRatUp$ source rows, the even/odd $\StreamNameUp$ interlacing schedule, the $\DyadicRatCoreUp$ tolerance ledger, and the $\CauchyTailEquivalenceUp$ handoff. Consequently the seal cannot be used as a shortcut to quotient stream equality, selected limits, countable choice, host limit existence, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}

\begin{proof}
Read the seal row $R$ from an accepted carrier. By the carrier definition, $R$ is downstream of $A,B,W,D,T$ and records only the Real-facing boundary reached from those displayed rows.

The replay row $C$ has no branch beginning at $R$. It replays the route from the two regular rational sources through the even/odd schedule, dyadic tolerance ledger, and tail-equivalence handoff before the seal can be consumed.

The transport and provenance rows $H$ and $P$ preserve that route componentwise, and the local name $N$ names only the displayed interlacing packet. Hence no excluded host object can escape through the Real seal.
\end{proof}

\falsifiablePrediction{Every $\CauchyInterlacingUp$ Real-facing read factors through two RegSeqRat source rows, one even/odd StreamName schedule, one DyadicRatCore tolerance ledger, one CauchyTailEquivalence handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, local naming, and one terminal RealUp seal.}

\independenceWitness{streamname, regseqrat, dyadicratcore, cauchy-tail-equivalence, real: $\CauchyInterlacingUp$ is not bijective to any listed sibling because it jointly carries two regular rational source rows, an even/odd interlacing schedule, a dyadic tolerance ledger, one tail-equivalence handoff, structural transport, replay, provenance, local naming, and a single Real-facing seal.}

\closureat{CauchyInterlacingUp}{seedStr}

\begin{closurestatus}{\CauchyInterlacingUp}
  \constructivestory{A $\CauchyInterlacingUp$ packet is generated from two RegSeqRat source rows, one even/odd StreamName schedule, one DyadicRatCore tolerance ledger, one CauchyTailEquivalence handoff, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-interlacing-carrier}, \autoref{thm:cauchy-interlacing-namecert-obligations}, \autoref{thm:cauchy-interlacing-regseqrat-handoff}, and \autoref{thm:cauchy-interlacing-real-seal-nonescape} seed the finite constructive route for merging two regular rational names into one Real-facing seal.}
  \formalstatus{\formalTargetV}
  \leantarget{BEDC.Derived.CauchyInterlacingUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, quotient stream equality, selected limits, countable choice, host sequence limits, trichotomy, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, even/odd schedule discipline, dyadic tolerance exactness, CauchyTailEquivalence handoff, real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CauchyInterlacingUp.}
\end{closurestatus}
