\chapter{A Concrete Naming Certificate for $\ContinuationCountermodelUp$}
\label{ch:concrete-instances-continuationcountermodel-namecert}
\origin{ai}

The $\ContinuationCountermodelUp$ packet realizes the open-continuation refusal surface of \autoref{sec:physical-induction-open-continuation} as a finite counter-continuation certificate. It sits beside the physical-induction packet of \autoref{ch:concrete-instances-reality-constrained-physical-induction-namecert}, the stability seal of \autoref{ch:concrete-instances-physical-induction-stability-seal-namecert}, the law certificate of \autoref{ch:concrete-instances-law-certificate-namecert}, the open-fit packet of \autoref{ch:concrete-instances-reality-constrained-open-fit-namecert}, and the failure surface of \autoref{ch:concrete-instances-realityconstrainedfailuresurface-namecert}. Those chapters supply fit, reuse, law, and defeat rows; this packet stores the single finite continuation route where predictive reuse is refused.

\begin{definition}[ContinuationCountermodel carrier]
\label{def:continuationcountermodel-carrier}
A $\ContinuationCountermodelUp$ carrier is a finite $\BHist$ packet
$$
C=(F,U,M,O,K,S,E,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite-fit row recording the observed prefix, classifier, and model agreement used by the proposed reuse claim;
\item $U$ is the admissible-continuation row naming the continuation class being tested;
\item $M$ is the model-prediction row exported from the fitted model along $U$;
\item $O$ is the observed-continuation row recorded on the same continuation route;
\item $K$ is the mismatch and counter-row comparing $M$ with $O$ at the displayed continuation;
\item $S$ is the stability-certificate row whose reuse claim is being tested;
\item $E$ is the failure-surface row recording the displayed defeat of predictive reuse;
\item $H$ records componentwise $\hsame$ transport for $F,U,M,O,K,S,E,R,P,N$;
\item $R$ is the displayed replay route tying the finite fit, prediction, observed continuation, mismatch, stability basis, and failure surface into one counter-continuation;
\item $P$ is the $\Pkg$ provenance over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, and the sibling physical-induction, stability-seal, law-certificate, open-fit, and failure-surface rows;
\item $N$ is the local $\NameCert_{\ContinuationCountermodelUp}$ row.
\end{enumerate}
The classifier accepts only packets displaying all eleven rows. It has no coordinate for final empirical truth, global model failure, unbounded future history, hidden continuation choice, or predictive reuse beyond the counter-continuation route in $R$.
\end{definition}
\leandef{BEDC.Derived.ContinuationCountermodelUp.ContinuationCountermodelUp}
\leanchecked{BEDC.Derived.ContinuationCountermodelUp.ContinuationCountermodelTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ContinuationCountermodel NameCert obligations]
\label{thm:continuationcountermodel-namecert-obligations}
For the carrier of \autoref{def:continuationcountermodel-carrier}, the local $\NameCert_{\ContinuationCountermodelUp}$ surface is exhausted by five obligation rows:
\begin{enumerate}
\item carrier admission for $C=(F,U,M,O,K,S,E,H,R,P,N)$;
\item finite-fit and admissible-continuation exposure through $F$ and $U$;
\item prediction and observation comparison through $M,O,K$;
\item stability-certificate and failure-surface exposure through $S$ and $E$;
\item componentwise transport, replay, provenance, and local naming through $H,R,P,N$.
\end{enumerate}
Every accepted counter-continuation must display these rows before it can defeat predictive reuse for the stated continuation class.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:continuationcountermodel-carrier}. The row list displays the finite fit, admissible continuation, model prediction, observed continuation, mismatch row, stability certificate, failure surface, transport, replay, provenance, and local name.

The first two obligations bind the source of the reuse claim: $F$ supplies only finite fit, and $U$ names only the continuation class under test. They do not export a global future-success or global future-failure claim.

The comparison obligation is carried by $M,O,K$. The model prediction and observed continuation are both read on the displayed route, and $K$ records the separating row that blocks predictive reuse for that continuation.

The stability and failure rows $S,E$ then place the mismatch against the exact certificate being tested. Transport, replay, provenance, and local naming through $H,R,P,N$ keep the countermodel inside the same finite packet. Since no further coordinate is present, the five rows exhaust the local NameCert surface.
\end{proof}
\leanchecked{BEDC.Derived.ContinuationCountermodelUp.ContinuationCountermodelNameCertObligations}

\begin{theorem}[ContinuationCountermodel predictive-reuse defeat]
\label{thm:continuationcountermodel-predictive-reuse-defeat}
An accepted $\ContinuationCountermodelUp$ packet rejects predictive reuse for the displayed continuation class whenever $F$ matches the finite fit row, $U$ admits the tested continuation, and the counter-row $K$ records a mismatch between the model prediction $M$ and the observed continuation $O$. The rejection is local to the route $R$ and does not assert global model failure outside the displayed packet.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:continuationcountermodel-namecert-obligations}. They require $F,U,M,O,K,S,E,H,R,P,N$ to be read together before a counter-continuation is accepted.

The rows $F$ and $U$ keep the source finite fit and continuation class visible. Thus the packet does not reject the model merely because a different continuation or a different finite-fit row exists.

The rows $M,O,K$ supply the defeating comparison. Once $K$ displays the mismatch between the prediction and the observed continuation on the same route, the stability certificate $S$ cannot be reused as a predictive license for that continuation class.

Finally $E,H,R,P,N$ localize the defeat to the displayed failure surface, transport, replay route, provenance, and local name. The packet therefore defeats predictive reuse on that route without claiming a final oracle about every possible continuation.
\end{proof}
\leanchecked{BEDC.Derived.ContinuationCountermodelUp.ContinuationCountermodelUp\_root\_replay\_transport}

\begin{theorem}[ContinuationCountermodel replay non-escape]
\label{thm:continuationcountermodel-replay-nonescape}
Every consumer of an accepted $\ContinuationCountermodelUp$ packet must read the counter-continuation through
$$
F,U,M,O,K,S,E,H,R,P,N.
$$
No consumer may detach the mismatch row from the finite fit, admissible continuation, stability certificate, failure surface, replay route, provenance, or local naming row and then treat it as an unbounded physical-law refutation.
\end{theorem}
\begin{proof}
Use the carrier definition. The mismatch row $K$ is one coordinate of the finite packet, not an independent global falsifier.

Apply \autoref{thm:continuationcountermodel-predictive-reuse-defeat}. The predictive-reuse rejection depends on $F,U,M,O,K,S,E$ being read along the replay route $R$.

The transport and provenance rows $H,P$ preserve that same packet, and $N$ names it locally. Because no coordinate exports unbounded physical-law refutation, hidden continuation choice, or global model failure, a consumer that detaches $K$ from the displayed packet leaves the accepted surface.
\end{proof}

The later Lean file \texttt{lean4/BEDC/Derived/ContinuationCountermodelUp/TasteGate.lean} must provide explicit $\mathsf{Nontrivial}\ \ContinuationCountermodelUp$ and $\mathsf{FieldFaithful}\ \ContinuationCountermodelUp$ instances preserving $F,U,M,O,K,S,E,H,R,P,N$.

\falsifiablePrediction{A continuation packet with matching finite fit but a displayed mismatch row is rejected as predictive reuse for that continuation class.}

\independenceWitness{realityconstrainedphysicalinduction, physicalinductionstabilityseal, lawcertificate, realityconstrainedfailuresurface, realityconstrainedopenfit: none is bijective because ContinuationCountermodelUp stores the single counter-continuation route tying finite fit, prediction, observed continuation, mismatch row, stability basis, failure surface, replay, provenance, and local naming in one packet.}

\closureat{ContinuationCountermodelUp}{seedStr}

\begin{closurestatus}{\ContinuationCountermodelUp}
  \constructivestory{A $\ContinuationCountermodelUp$ packet is generated from finite fit, admissible continuation, model prediction, observed continuation, mismatch, stability certificate, failure surface, componentwise transport, replay, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:continuationcountermodel-carrier}, \autoref{thm:continuationcountermodel-namecert-obligations}, \autoref{thm:continuationcountermodel-predictive-reuse-defeat}, and \autoref{thm:continuationcountermodel-replay-nonescape} bind the finite counter-continuation carrier, five-row NameCert surface, predictive-reuse defeat, and replay non-escape theorem.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, global model failure, total physical-law refutation, final empirical truth, or continuations outside the displayed route.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-fit exposure, continuation admission, prediction and observation comparison, mismatch exposure, stability and failure-surface exposure, replay, provenance, local naming, TasteGate nontriviality, and field faithfulness for $F,U,M,O,K,S,E,H,R,P,N$.}
\end{closurestatus}
