\chapter{A Concrete Naming Certificate for $\RealTailDiameterGaugeUp$}
\label{ch:concrete-instances-real-tail-diameter-gauge-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealTailDiameterGaugeUp$ packet records the finite gauge by which a real-facing consumer reads a regular rational tail only after the displayed tail-diameter, dyadic tolerance, stream-window, and readback rows have been exposed. It sits after the tail-diameter witness of \autoref{ch:concrete-instances-cauchy-tail-diameter-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window service of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a non-quotient L10 gauge object for Real and Completion consumers; it is not host real equality, quotient stream equality, selected limits, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Real tail-diameter gauge BHist source]
\label{def:real-tail-diameter-gauge-bhist-source}
A $\RealTailDiameterGaugeUp$ carrier is a finite $\BHist$ packet
$$
G=(E,T,D,W,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the $\RealUp$ seal row naming the real-facing boundary that the gauge is allowed to serve.
\item $T$ is the $\CauchyTailDiameterUp$ ledger row, recording the inspected tail threshold, two visible tail indices, and the displayed diameter bound.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row consumed by the same tail-diameter ledger.
\item $W$ is the $\StreamNameUp$ window row that exposes the finite source observations inspected by $T$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same window and tolerance data before any real-facing read is accepted.
\item $H$ records componentwise $\hsame$ transport for the seal, tail-diameter ledger, dyadic tolerance, window, readback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a real-facing gauge request through $E,T,D,W,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RealTailDiameterGaugeUp$, $\RealUp$, $\CauchyTailDiameterUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealTailDiameterGaugeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $E,T,D,W,R,H,C,P,N$. It has no coordinate for host real equality, quotient stream equality, selected limits, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Real tail-diameter gauge NameCert obligation surface]
\label{thm:real-tail-diameter-gauge-namecert-obligation-surface}
For every accepted $\RealTailDiameterGaugeUp$ carrier
$$
G=(E,T,D,W,R,H,C,P,N),
$$
the local $\NameCert_{\RealTailDiameterGaugeUp}$ surface consists exactly of carrier admission for the $\RealUp$ seal row $E$, the $\CauchyTailDiameterUp$ ledger row $T$, the $\DyadicRatCoreUp$ tolerance row $D$, the $\StreamNameUp$ window row $W$, the $\RegSeqRatUp$ readback row $R$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and local naming $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-tail-diameter-gauge-bhist-source}. The analytic rows are the Real seal $E$, tail-diameter ledger $T$, dyadic tolerance $D$, finite window $W$, and regular rational readback $R$.

The gauge obligation is read only through $T,D,W,R$. The tail-diameter ledger records the visible tail request and bound, the dyadic row supplies the tolerance budget, the stream row exposes the inspected finite windows, and the regular row repacks the same data for rational readback.

The structural rows $H,C,P,N$ preserve that route under transport, replay, provenance, and naming. Since the carrier has no coordinate for the excluded host or completion objects, the displayed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real tail-diameter gauge RegSeqRat handoff]
\label{thm:real-tail-diameter-gauge-regseqrat-handoff}
Every $\RegSeqRatUp$ or $\RealUp$ consumer exported by an accepted $\RealTailDiameterGaugeUp$ packet factors through
$$
W,D \longmapsto T \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
Thus a Real and Completion route may read the finite stream window, dyadic tolerance ledger, tail-diameter gauge, regular rational handoff, terminal Real seal, transport, replay, provenance, and local naming rows, but it receives no host real equality, quotient stream equality, selected limit, trichotomy decision, countable-choice schedule, ambient $\RealUp$ completeness theorem, Lean verification, or bridge check.
\end{theorem}
\begin{proof}
Start with an exported regular-rational or real-facing read. The only finite observations available to the packet are the $\StreamNameUp$ row $W$ and the $\DyadicRatCoreUp$ tolerance row $D$.

The tail-diameter ledger $T$ then binds those observations to a displayed tail request and diameter bound. This row is the gauge that prevents a consumer from replacing the finite tail evidence by a quotient stream or a selected limit.

Only after $T$ is displayed does the handoff expose the $\RegSeqRatUp$ row $R$ and the $\RealUp$ seal row $E$. The readback and seal are therefore downstream from the same finite gauge data.

Finally $H,C,P,N$ transport, replay, source, and name the route. Since the excluded objects do not occur in the carrier, no consumer can bypass the displayed handoff.
\end{proof}

\closureat{RealTailDiameterGaugeUp}{seedStr}

\begin{closurestatus}{\RealTailDiameterGaugeUp}
  \constructivestory{A $\RealTailDiameterGaugeUp$ packet is generated from a RealUp seal row, a CauchyTailDiameterUp ledger, a DyadicRatCore tolerance row, a StreamName window row, a RegSeqRat readback row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-tail-diameter-gauge-bhist-source}, \autoref{thm:real-tail-diameter-gauge-namecert-obligation-surface}, and \autoref{thm:real-tail-diameter-gauge-regseqrat-handoff} seed the finite real-facing tail-diameter gauge for regular rational and completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host real equality, quotient stream equality, selected limits, trichotomy, countable choice, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Real seal confinement, CauchyTailDiameter ledger exactness, DyadicRatCore tolerance readback, StreamName window coverage, RegSeqRat handoff, transport stability, continuation replay, provenance non-escape, and local naming for BEDC.Derived.RealTailDiameterGaugeUp.}
\end{closurestatus}
