\chapter{A Concrete Naming Certificate for $\CauchyCompletionDenseEmbeddingUp$}
\label{ch:concrete-instances-cauchy-completion-dense-embedding-namecert}
\origin{human}

Following Bishop and Bridges on constructive completions and Bourbaki/Kelley on dense embeddings, the $\CauchyCompletionDenseEmbeddingUp$ packet records the finite dense-source route by which a Cauchy completion consumer reads a source object inside its completion boundary. It sits beside the dense uniform embedding surface of \autoref{ch:concrete-instances-dense-uniform-embedding-namecert}, the functorial Cauchy-completion route of \autoref{ch:concrete-instances-cauchy-completion-functoriality-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies dense embedding data for completion consumers without asserting quotient completion equality, selected representatives, countable choice, or $\RealUp$ completeness.

\begin{definition}[Cauchy completion dense-embedding carrier]
\label{def:cauchy-completion-dense-embedding-carrier}
A $\CauchyCompletionDenseEmbeddingUp$ carrier is a finite $\BHist$ packet
$$
J=(A,G,K,S,D,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the dense source row. It records the source-side Cauchy observations that a completion consumer may approximate by displayed source data.
\item $G$ is the embedding graph row. It records the displayed source-to-completion graph and the finite image-window reads used by dense embedding consumers.
\item $K$ is the Cauchy completion row, read through the completion-facing route associated with $\CauchyCompletionFunctorialityUp$.
\item $S$ is the $\StreamNameUp$ row exposing the finite request windows inspected by the source and completion sides.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to compare source-image windows with completion windows.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the same windows and dyadic tolerances.
\item $E$ is the terminal $\RealUp$ seal row, reachable only after $A,G,K,S,D,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the dense source, embedding graph, completion, window, tolerance, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a dense-source request through $A,G,K,S,D,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionDenseEmbeddingUp$, $\DenseUniformEmbeddingUp$, $\CauchyCompletionFunctorialityUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCompletionDenseEmbeddingUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for quotient completion equality, selected representatives, countable choice, host equality of completion classes, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy completion dense-embedding NameCert obligations]
\label{thm:cauchy-completion-dense-embedding-namecert-obligations}
For every accepted $\CauchyCompletionDenseEmbeddingUp$ carrier
$$
J=(A,G,K,S,D,Q,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyCompletionDenseEmbeddingUp}$ surface consists exactly of carrier admission for the dense source row, embedding graph row, Cauchy completion row, $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every completion-facing dense read must expose $A,G,K,S,D,Q$ before $E,H,C,P,N$ can be consumed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-completion-dense-embedding-carrier}. The dense source, embedding graph, Cauchy completion row, finite windows, tolerance ledger, regular readback, and Real seal are exactly the displayed analytic coordinates.

The dense-source route is read through $A,G,K$. A completion consumer first fixes the source row, then the embedding graph row, and only then the completion-facing row associated with the Cauchy completion route.

The finite observation route is read through $S,D,Q$. The stream windows expose inspected requests, the dyadic ledger supplies the tolerance budget, and the regular rational readback repacks the same observations before any Real-facing seal is visible.

Finally $E,H,C,P,N$ preserve and name the route. Since quotient completion equality, selected representatives, countable choice, host equality, and ambient completeness have no carrier coordinate, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Cauchy completion dense-embedding Real seal handoff]
\label{thm:cauchy-completion-dense-embedding-real-seal-handoff}
Every $\RealUp$ or completion consumer exported by an accepted $\CauchyCompletionDenseEmbeddingUp$ packet factors through
$$
\DenseUniformEmbeddingUp,\ \CauchyCompletionFunctorialityUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp .
$$
More precisely, the consumer reads the dense source row $A$, embedding graph $G$, Cauchy completion row $K$, finite windows $S$, tolerance ledger $D$, regular readback $Q$, terminal seal $E$, componentwise transport $H$, displayed replay $C$, provenance $P$, and local name $N$ before the real-facing boundary is exposed.
\end{theorem}
\begin{proof}
Start with an exported Real-facing or completion-facing read. The NameCert obligations of \autoref{thm:cauchy-completion-dense-embedding-namecert-obligations} force the read through $A,G,K$ before the finite observation rows can be consumed.

Read the sibling routes next. The dense source is the $\DenseUniformEmbeddingUp$ surface, the completed-map side is routed through $\CauchyCompletionFunctorialityUp$, and the finite observations are the $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ rows displayed by the carrier.

Only after those rows have been displayed can the terminal $\RealUp$ seal row $E$ be read. The structural rows $H,C,P,N$ transport, replay, source, and name the same route, so the handoff exports no quotient completion equality, selected representative, countable-choice selector, host equality, or ambient $\RealUp$ completeness theorem.
\end{proof}

\closureat{CauchyCompletionDenseEmbeddingUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionDenseEmbeddingUp}
  \constructivestory{A $\CauchyCompletionDenseEmbeddingUp$ packet is generated from a dense source row, embedding graph row, Cauchy completion row, StreamName windows, DyadicRatCore tolerance ledger, RegSeqRat readback, terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-dense-embedding-carrier}, \autoref{thm:cauchy-completion-dense-embedding-namecert-obligations}, and \autoref{thm:cauchy-completion-dense-embedding-real-seal-handoff} seed the dense-source route for Cauchy completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion equality, selected representatives, countable choice, host equality of completion classes, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense source exposure, embedding graph exactness, Cauchy completion handoff, StreamName window coverage, DyadicRatCore tolerance readback, RegSeqRat handoff, Real seal confinement, transport, replay, provenance, and local naming for BEDC.Derived.CauchyCompletionDenseEmbeddingUp.}
\end{closurestatus}
