\chapter{A Concrete Naming Certificate for $\BishopLocatedRealFilterUp$}
\label{ch:concrete-instances-bishop-located-real-filter-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopLocatedRealFilterUp$ packet records the finite filter-facing route by which located real brackets are read through dyadic tolerances, stream windows, regular rational readback, and the terminal real seal. It consumes the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the located bracket surface of \autoref{ch:concrete-instances-located-real-interval-namecert}, and the selector boundary of \autoref{ch:concrete-instances-cauchy-filter-selector-namecert}. The packet gives the L10 Real and Completion route a located filter interface without asserting quotient filter equality, host real equality, selected limit points, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop located real filter carrier]
\label{def:bishop-located-real-filter-carrier}
A $\BishopLocatedRealFilterUp$ carrier is a finite packet
$$
S=(F,L,D,W,R,E,B,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the filter-base row, exposing the finite base request, refinement evidence, and Cauchy-facing filter data that a later completion consumer may inspect.
\item $L$ is the located-real bracket row, recording lower and upper bracket reads over $\LocatedRealIntervalUp$ together with the displayed apartness and containment data used to locate the requested real value.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger governing bracket width, filter-base comparison, stream-window radius, and regular-rational readback.
\item $W$ is the $\StreamNameUp$ window row attached to the filter request and the located bracket.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the windows in $W$ under the tolerance ledger $D$.
\item $E$ is the $\RealUp$ seal row, available only after $F,L,D,W,R$ have been displayed and replayed.
\item $B$ is the $\BHist$ history row recording the finite route from the filter request through the located bracket, tolerance ledger, stream windows, regular readback, and Real seal.
\item $H$ records componentwise $\hsame$ transport for $F,L,D,W,R,E,B,T,P,N$.
\item $T$ records displayed $\Cont$ replay from every located filter request through $F,L,D,W,R,E,B,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopLocatedRealFilterUp$, $\LocatedRealIntervalUp$, $\CauchyFilterSelectorUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopLocatedRealFilterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,L,D,W,R,E,B,H,T,P,N$. It has no coordinate for quotient filter equality, host selected representatives, host real equality, countable choice, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Bishop located real filter NameCert obligations]
\label{thm:bishop-located-real-filter-namecert-obligations}
For every accepted $\BishopLocatedRealFilterUp$ carrier $S=(F,L,D,W,R,E,B,H,T,P,N)$, the local $\NameCert_{\BishopLocatedRealFilterUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the filter base, located-real bracket, dyadic tolerance ledger, StreamName windows, RegSeqRat readback, Real seal, history, transport, replay, provenance, and local naming row;
\item bracket exactness, requiring each located-real bracket read in $L$ to be witnessed by displayed $\LocatedRealIntervalUp$ endpoint and containment data;
\item filter-base stability, requiring refinements of $F$ to preserve the same located bracket and tolerance ledger through $\BHist$ and $\hsame$ transport;
\item dyadic ledger stability, requiring $D$ to control the bracket width, stream-window radius, and regular-rational readback without adding an external modulus;
\item StreamName and RegSeqRat handoff, requiring every numeric read to pass through $W$ and then $R$ before the terminal seal $E$ can be consumed;
\item nonescape, excluding quotient filters, host-selected representatives, countable choice, host real equality, selected limiting points, and ambient Real completeness.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:bishop-located-real-filter-carrier}. The accepted packet displays the filter base, located bracket, dyadic ledger, stream windows, regular readback, Real seal, history, transport, replay, provenance, and local naming rows.

Bracket exactness is row-local. The bracket row $L$ can expose only the endpoint and containment data already carried by $\LocatedRealIntervalUp$, so it cannot identify a real by host order equality or by a selected representative.

The filter-base and tolerance rows then fix the route. Refinement of $F$ is transported through $B$ and $H$, while the same dyadic row $D$ governs bracket width, window radius, and readback precision.

Finally the numeric handoff is ordered by $W,R,E$. Stream windows are read before regular rational data, and regular rational data are read before the terminal $\RealUp$ seal. Since no excluded host object is a carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bishop located real filter L10 handoff]
\label{thm:bishop-located-real-filter-l10-handoff}
Every L10 Real or Completion consumer of an accepted $\BishopLocatedRealFilterUp$ packet $S=(F,L,D,W,R,E,B,H,T,P,N)$ must read the finite route
$$
F,L,D,W,R \longmapsto E \longmapsto B,H,T,P,N
$$
before it treats the request as Real-facing or completion-facing data. Thus the packet supplies a filter-based located-real handoff to $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\LocatedRealIntervalUp$, and $\CauchyFilterSelectorUp$ consumers without asserting ambient real completeness or quotient equality of filters.
\end{theorem}
\begin{proof}
Read the carrier rows in order. A consumer first receives the filter base $F$ and the located bracket $L$, while the dyadic ledger $D$ supplies the common tolerance budget.

The numerical content is then exposed through $W$ and $R$. The $\StreamNameUp$ row records finite observation windows, and the $\RegSeqRatUp$ row records the regular rational readback extracted from those windows.

Only after these rows are displayed can the Real seal $E$ be consumed. The history, transport, replay, provenance, and local naming rows $B,H,T,P,N$ preserve that order for later L10 Real and Completion routes.

The carrier has no quotient-filter equality, selected representative, host real equality, choice schedule, or ambient completeness coordinate. Therefore every downstream handoff factors through the displayed finite route.
\end{proof}

\begin{closurestatus}{\BishopLocatedRealFilterUp}
  \constructivestory{A $\BishopLocatedRealFilterUp$ packet is generated from a displayed filter base, a located-real bracket, a dyadic tolerance ledger, finite StreamName windows, RegSeqRat readback, a Real seal, BHist history, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-located-real-filter-carrier}, \autoref{thm:bishop-located-real-filter-namecert-obligations}, and \autoref{thm:bishop-located-real-filter-l10-handoff} seed the finite filter-facing located-real interface for the L10 Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filter equality, ambient Real completeness, selected limits, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Lean closure requires carrier admission, bracket exactness, filter-base stability, dyadic ledger stability, StreamName and RegSeqRat handoff, and Real seal boundary for BEDC.Derived.BishopLocatedRealFilterUp.}
\end{closurestatus}
