\chapter{A Concrete Naming Certificate for $\PrivateSharedDecorationModelUp$}
\label{ch:concrete-instances-private-shared-decoration-model-namecert}
\origin{ai}

The $\PrivateSharedDecorationModelUp$ packet realizes the private/shared decoration theorem of \autoref{thm:philosophy-private-shared-decoration-theorem} inside the boundary-tile source of \autoref{subsec:philosophy-dna-window-six-boundary-tiles}. It sits beside the DNA boundary-tile packet of \autoref{ch:concrete-instances-dna-window-six-boundary-tile-namecert}, the trigger-threshold packet of \autoref{ch:concrete-instances-dna-window-six-trigger-threshold-namecert}, and the finite trigger algebra route of \autoref{ch:concrete-instances-window-coverage-trigger-algebra-namecert}. The packet records private blocks, shared rows, lift counts, and defect ledgers as finite NameCert data; it is not a biological mechanism, stochastic evolution model, hidden enumeration oracle, or quotient codon semantics.

\begin{definition}[PrivateSharedDecorationModel carrier]
\label{def:private-shared-decoration-model-carrier}
A $\PrivateSharedDecorationModelUp$ carrier is a finite $\BHist$ packet
$$
M=(B,S,L,D,T,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the nonempty private-block row, recording the partition of coordinates that remain private to a single decorated support.
\item $S$ is the shared-row ledger, assigning every shared coordinate to a finite row set of size at least two.
\item $L$ is the lift-count row, recording the finite $\ell^{m}$ lift factor attached to displayed support blocks.
\item $D$ is the defect ledger, recording the row-set size contribution to the defect-refined polynomial.
\item $T$ records componentwise $\hsame$ transport for $B,S,L,D,R,P,N$.
\item $R$ records displayed $\Cont$ replay from a decorated trigger request through the private block, shared rows, lift count, defect ledger, provenance, and local naming rows.
\item $P$ is the $\Pkg$ provenance over $\PrivateSharedDecorationModelUp$, $\DnaWindowSixBoundaryTileUp$, $\DNAWindowSixTriggerThresholdUp$, $\WindowCoverageTriggerAlgebraUp$, the source theorem of \autoref{thm:philosophy-private-shared-decoration-theorem}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PrivateSharedDecorationModelUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,S,L,D,T,R,P,N$. It has no coordinate for biological mechanism, stochastic fitness, quotient codon equality, hidden global semantics, or an unrecorded enumeration oracle.
\end{definition}

\begin{theorem}[PrivateSharedDecorationModel NameCert obligations]
\label{thm:private-shared-decoration-model-namecert-obligations}
For every accepted $\PrivateSharedDecorationModelUp$ carrier
$$
M=(B,S,L,D,T,R,P,N),
$$
the local $\NameCert_{\PrivateSharedDecorationModelUp}$ surface consists exactly of carrier admission for the nonempty private-block row, shared-row ledger, lift-count row, defect ledger, componentwise transport, displayed replay, provenance, and local naming. A decorated trigger read is accepted only after it exposes a nonempty private block and assigns every shared coordinate to at least two rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:private-shared-decoration-model-carrier}. The private block, shared-row ledger, lift count, defect ledger, transport, replay, provenance, and local name are exactly the displayed coordinates.

The private/shared constraint is read through $B,S$. The row $B$ must display a nonempty private partition, and the ledger $S$ must attach every shared coordinate to a row set of size at least two.

The enumeration and defect data are read through $L,D$. The lift-count row records the finite lift factor, while the defect ledger records the shared-row contribution used by the source theorem.

Finally $T,R,P,N$ transport, replay, source, and name the same route. Since biological mechanism, stochastic fitness, quotient codon equality, hidden global semantics, and unrecorded enumeration have no carrier coordinate, the listed rows exhaust the NameCert obligations.
\end{proof}

\falsifiablePrediction{If a displayed decorated trigger lacks a nonempty private block or assigns a shared coordinate to fewer than two rows, it is rejected by the local NameCert.}

\independenceWitness{dna-window-six-boundary-tile, dna-window-six-trigger-threshold, dna-window-six-translation-boundary: $\PrivateSharedDecorationModelUp$ is not bijective to any listed sibling because this packet jointly carries private-block rows, shared-row ledgers, lift-count rows, defect ledgers, transport, replay, provenance, and local naming.}

The Lean TasteGate route for \texttt{BEDC.Derived.PrivateSharedDecorationModelUp} must provide explicit $\Nontrivial\ \PrivateSharedDecorationModelUp$ and $\FieldFaithful\ \PrivateSharedDecorationModelUp$ instances preserving $B,S,L,D,T,R,P,N$ as separate displayed fields.

\closureat{PrivateSharedDecorationModelUp}{seedStr}

\begin{closurestatus}{\PrivateSharedDecorationModelUp}
  \constructivestory{A $\PrivateSharedDecorationModelUp$ packet is generated from a nonempty private-block row, shared-row ledger, lift-count row, defect ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:private-shared-decoration-model-carrier} and \autoref{thm:private-shared-decoration-model-namecert-obligations} seed the finite private/shared decoration packet over DNA boundary-tile trigger rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close biological mechanism, stochastic evolution, quotient codon equality, hidden global semantics, unrestricted enumeration, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, private-block nonemptiness, shared-row arity, lift-count exposure, defect-ledger exposure, transport, replay, provenance, local naming, Nontrivial PrivateSharedDecorationModelUp, and FieldFaithful PrivateSharedDecorationModelUp for BEDC.Derived.PrivateSharedDecorationModelUp.}
\end{closurestatus}
