\chapter{A Concrete Naming Certificate for $\ConstructiveCantorTheoremUp$}
\label{ch:concrete-instances-constructive-cantor-theorem-namecert}
\origin{human}

Following Cantor and Bishop--Bridges, the $\ConstructiveCantorTheoremUp$ packet records the finite diagonal obstruction to enumerating Cantor-space bit names. It sits over the binary prefix carrier of \autoref{ch:concrete-instances-cantorspace-namecert}, the finite bar-facing tree discipline of \autoref{ch:concrete-instances-kleene-tree-namecert}, the fan-theoretic bounded-window route of \autoref{ch:concrete-instances-fantheorem-namecert}, and the Real-facing non-surjection boundary of \autoref{ch:concrete-instances-real-diagonal-non-surjection-namecert}. The packet names only finite rows: an attempted enumeration window, its displayed diagonal bit schedule, the disagreement row at each inspected index, and the no-enumeration handoff. It is not a host-cardinality theorem, not a completed powerset construction, and not a quotient-stream principle.

\begin{definition}[Constructive Cantor finite diagonal carrier]
\label{def:constructive-cantor-finite-diagonal-carrier}
A $\ConstructiveCantorTheoremUp$ carrier is a finite $\BHist$ packet
$$
K=(E,W,D,G,T,F,R,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $E$ is the displayed finite enumeration attempt row, listing the first $n$ candidate Cantor-space names through finite prefix windows;
\item $W$ is the finite binary observation window, naming the inspected coordinates and the finite prefix depth used for each candidate;
\item $D$ is the diagonal-bit row, obtained by flipping the displayed $i$th bit of the $i$th candidate whenever that coordinate is present in $W$;
\item $G$ is the disagreement ledger, recording for every inspected index $i<n$ that the diagonal row disagrees with the $i$th candidate at the displayed coordinate;
\item $T$ is the tree-read row through $\KleeneTreeUp$, ensuring that finite prefix extension and absence of a completed path are read as finite branch data;
\item $F$ is the fan-window row through $\FanTheoremUp$, recording the bounded prefix surface consumed by any compact Cantor-space handoff;
\item $R$ is the Real-facing route through $\RealDiagonalNonSurjectionUp$, used only after the Cantor-space disagreement ledger has been displayed;
\item $H$ records componentwise $\hsame$ transport for enumeration rows, prefix windows, diagonal bits, disagreement ledgers, tree rows, fan rows, Real-facing routes, replay rows, provenance, and local naming;
\item $C$ records displayed $\Cont$ replay from an enumeration window to diagonal-bit construction, disagreement verification, Cantor-space handoff, and Real-facing non-surjection routing;
\item $P$ is the $\Pkg$ provenance over $\ConstructiveCantorTheoremUp$, $\CantorSpaceUp$, $\KleeneTreeUp$, $\FanTheoremUp$, $\RealDiagonalNonSurjectionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\ConstructiveCantorTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $E,W,D,G,T,F,R,H,C,P,N$. It has no coordinate for a completed enumeration of all binary streams, host powersets, quotient stream equality, countable choice, or classical cardinal comparison.
\end{definition}

\begin{theorem}[Finite diagonal obligations]
\label{thm:constructive-cantor-finite-diagonal-obligations}
For every accepted $\ConstructiveCantorTheoremUp$ carrier $K=(E,W,D,G,T,F,R,H,C,P,N)$, the local $\NameCert_{\ConstructiveCantorTheoremUp}$ surface consists exactly of finite enumeration-window admission through $E$, binary observation through $W$, diagonal-bit formation through $D$, inspected-index disagreement through $G$, tree and fan routing through $T,F$, Real-facing non-surjection routing through $R$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.ConstructiveCantorTheoremUp.ConstructiveCantorTheoremTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier of \autoref{def:constructive-cantor-finite-diagonal-carrier}. The enumeration and observation rows are $E$ and $W$, so every candidate read is confined to a displayed finite prefix window.

Build the diagonal row by induction on the finite index spine of $W$. The empty window contributes no bit and no disagreement row. At a successor index, read the displayed candidate bit at the diagonal coordinate and place the opposite bit in $D$.

The same induction fills $G$. Each successor step adds exactly the disagreement between the new diagonal bit and the candidate bit just inspected, while previous rows are transported componentwise by $H$ and replayed by $C$.

The rows $T,F,R$ do not add an infinite object. They only route the same finite disagreement ledger through the Kleene-tree, fan-window, and Real-facing non-surjection surfaces, so the listed rows exhaust the certificate without a host powerset, quotient stream equality, choice principle, or classical cardinal comparison.
\end{proof}

\begin{theorem}[No-enumeration window]
\label{thm:constructive-cantor-no-enumeration-window}
Let $K$ be an accepted $\ConstructiveCantorTheoremUp$ carrier with a displayed enumeration window $E$ of length $n$. The diagonal row $D$ determines a Cantor-space prefix window such that for every inspected index $i<n$, the $i$th candidate of $E$ differs from $D$ at the displayed diagonal coordinate recorded in $G$. Hence the window cannot certify that its listed candidates exhaust the displayed Cantor-space prefixes.
\end{theorem}
\begin{proof}
Induct on the finite enumeration window. For the empty window, there is no inspected candidate and the exhaustion claim has no displayed row.

At a successor window, the induction hypothesis supplies the disagreement rows for the previous candidates. The new candidate has a displayed diagonal coordinate in $W$, and the diagonal construction places the opposite binary value in $D$.

The new row of $G$ records this disagreement. Componentwise $\hsame$ transport preserves the previous rows and the displayed $\Cont$ replay keeps the construction inside the same finite packet.

Therefore every inspected candidate is separated from the diagonal prefix at its own displayed coordinate. A finite window containing these disagreement rows cannot also certify that the same listed candidates exhaust the displayed Cantor-space prefix surface.
\end{proof}

\begin{theorem}[Cantor-space handoff]
\label{thm:constructive-cantor-cantor-space-handoff}
Every downstream consumer of a $\ConstructiveCantorTheoremUp$ packet receives only the finite handoff formed by the enumeration window, binary observation window, diagonal-bit row, disagreement ledger, Kleene-tree row, fan-window row, Real-facing non-surjection route, transport, replay, provenance, and local naming. The handoff may be read by $\CantorSpaceUp$ and then by $\RealDiagonalNonSurjectionUp$, but it exports no completed stream quotient, powerset object, countable-choice selector, or classical uncountability principle.
\end{theorem}
\begin{proof}
Start with the finite rows $E,W,D,G$ of the carrier. By \autoref{thm:constructive-cantor-finite-diagonal-obligations}, these are the only rows that form and verify the diagonal disagreement.

Next read the Cantor-space side through \autoref{ch:concrete-instances-cantorspace-namecert}. The Kleene-tree and fan rows $T,F$ preserve finite prefix extension and bounded-window routing; they do not select a completed path or add an ambient compactness theorem.

Finally route the same disagreement ledger to \autoref{ch:concrete-instances-real-diagonal-non-surjection-namecert} through $R$. Since the carrier has no coordinate for quotient stream equality, countable choice, host powersets, or classical cardinal comparison, the consumer receives exactly the finite handoff named in the statement.
\end{proof}

\falsifiablePrediction{A purported $\ConstructiveCantorTheoremUp$ consumer that reads a no-enumeration conclusion while omitting the enumeration window, diagonal-bit row, inspected-index disagreement ledger, Cantor-space prefix row, transport, replay, provenance, or local naming refutes the packet.}

\independenceWitness{cantorspace, kleene-tree, fantheorem, real-diagonal-non-surjection: $\ConstructiveCantorTheoremUp$ is not bijective to any listed sibling because it jointly carries an attempted enumeration window, a diagonal-bit construction, an inspected-index disagreement ledger, and a downstream Cantor-space-to-Real non-surjection route in one finite NameCert packet.}

\closureat{ConstructiveCantorTheoremUp}{seedStr}

\begin{closurestatus}{\ConstructiveCantorTheoremUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:constructive-cantor-finite-diagonal-carrier}, \autoref{thm:constructive-cantor-finite-diagonal-obligations}, \autoref{thm:constructive-cantor-no-enumeration-window}, and \autoref{thm:constructive-cantor-cantor-space-handoff} seed the finite diagonal non-enumeration packet over Cantor-space prefix rows.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ConstructiveCantorTheoremUp.ConstructiveCantorTheoremTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a completed stream quotient, a host powerset object, a countable-choice selector, a classical cardinal comparison, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires Lean targets for carrier admission, diagonal-bit exactness, inspected-index disagreement, Cantor-space handoff, Real-facing route preservation, transport, replay, provenance, and local naming for BEDC.Derived.ConstructiveCantorTheoremUp.}
  \constructivestory{A $\ConstructiveCantorTheoremUp$ packet is generated from a finite attempted enumeration window, a finite binary observation window, a diagonal-bit row, an inspected-index disagreement ledger, Kleene-tree and fan-window rows, Real-facing non-surjection routing, componentwise transport, displayed replay, provenance, and a local NameCert row.}
\end{closurestatus}
