\chapter{A Concrete Naming Certificate for $\DedekindEtaCompletionUp$}
\label{ch:concrete-instances-dedekind-eta-completion-namecert}
\origin{human}

Following Bishop and Bridges on constructive real analysis, the $\DedekindEtaCompletionUp$ packet records an eta-completion route from regular rational names to located Dedekind-style real boundaries as finite BEDC NameCert data. It sits over the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Cauchy criterion equivalence surface of \autoref{ch:concrete-instances-cauchy-criterion-equivalence-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives completion consumers a displayed eta route without quotient streams, selected host limits, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[DedekindEtaCompletion carrier]
\label{def:dedekind-eta-completion-carrier}
A $\DedekindEtaCompletionUp$ carrier is a finite $\BHist$ packet
$$
E=(S,R,D,Q,L,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ finite-window schedule for the rational observations retained by the eta route.
\item $R$ is the $\RegSeqRatUp$ readback row, binding each retained stream window to a regular rational observation.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, carrying positive-radius witnesses, half-radius refinements, and strict comparison cells used by the regular readback.
\item $Q$ is the $\CauchyCriterionEquivalenceUp$ comparison row, recording the finite Cauchy criterion checks that certify the retained windows as a regular eta-family.
\item $L$ is the located lower-and-upper cut ledger generated from $S,R,D,Q$; it records only displayed rational cut tests and their dyadic slack.
\item $A$ is the terminal $\RealUp$ seal row, reachable only after the stream, regular, dyadic, criterion, and cut-ledger rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for the window, readback, tolerance, Cauchy criterion, cut-ledger, real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
S,R,D \longmapsto Q \longmapsto L \longmapsto A .
$$
\item $P$ is the $\Pkg$ provenance over $\DedekindEtaCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyCriterionEquivalenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindEtaCompletionUp}$ row.
\end{enumerate}
The carrier predicate admits exactly these ten rows. Its classifier compares accepted packets only through $S,R,D,Q,L,A,H,C,P,N$ and has no coordinate for quotient streams, selected host limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[DedekindEtaCompletion NameCert obligations]
\label{thm:dedekind-eta-completion-namecert-obligations}
For an accepted $\DedekindEtaCompletionUp$ carrier
$$
E=(S,R,D,Q,L,A,H,C,P,N),
$$
the local $\NameCert_{\DedekindEtaCompletionUp}$ surface consists exactly of the following finite obligations:
\begin{enumerate}
\item carrier admission for the stream-window schedule, regular rational readback, dyadic tolerance ledger, Cauchy criterion comparison row, located cut ledger, terminal real seal, transport, replay, provenance, and local naming rows;
\item window exactness, requiring every rational observation used by the eta route to be addressed by $S$ before it can be read by $R$;
\item dyadic tolerance exactness, requiring every comparison in the regular readback and every cut test in $L$ to consume a displayed tolerance or refinement from $D$;
\item Cauchy criterion compatibility, requiring $Q$ to certify the retained windows as the same regular eta-family before the cut ledger is exported;
\item cut locatedness, requiring $L$ to expose lower and upper rational tests only through $S,R,D,Q$;
\item real-seal handoff, requiring $A$ to be downstream of the same displayed eta route;
\item classifier transport and replay, requiring $H$ and $C$ to preserve exactly the listed rows and no external completion object;
\item non-escape, excluding quotient streams, selected host limits, countable choice, trichotomy, open-cover compactness, and ambient $\RealUp$ completeness.
\end{enumerate}
No NameCert obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dedekind-eta-completion-carrier}. The accepted packet exposes exactly the stream-window, regular readback, dyadic tolerance, Cauchy criterion, cut-ledger, real-seal, and structural rows.

Window exactness follows from the order of the carrier. A rational observation enters the eta route through $S$, and $R$ can read it only as a retained finite window. There is no coordinate for an unaddressed stream or a quotient of streams.

Dyadic tolerance exactness is supplied by $D$. Every regular comparison and every cut test has to name a positive-radius witness, refinement, or strict comparison cell before it can be used by $Q$ or $L$.

The Cauchy criterion row $Q$ is the only compatibility surface. It certifies that the retained regular windows form the eta-family consumed by the cut ledger, so no selected limit or countable-choice schedule is introduced.

The cut ledger $L$ is downstream of $S,R,D,Q$, and the real seal $A$ is downstream of $L$. Hence lower and upper rational tests and Real-facing reads remain inside the displayed eta route.

Finally $H,C,P,N$ transport, replay, source, and name only the listed rows. Since the excluded principles have no carrier coordinate, they cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[DedekindEtaCompletion L10 handoff]
\label{thm:dedekind-eta-completion-l10-handoff}
Every $\RealUp$ or completion-facing consumer of an accepted $\DedekindEtaCompletionUp$ carrier factors through the finite route
$$
\StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \CauchyCriterionEquivalenceUp \longmapsto \RealUp .
$$
The exported object is a displayed eta-completion handoff from regular rational windows to a located real seal. It is not a quotient stream, selected host limit, countable-choice construction, trichotomy split, open-cover compactness principle, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Start with the accepted carrier and project the public readback rows. A Real-facing or completion-facing consumer can reach the seal row $A$ only by following the replay route named in \autoref{def:dedekind-eta-completion-carrier}.

The first stage is finite-window data. The row $S$ names the inspected stream windows, and $R$ reads those windows as regular rational observations.

The second stage is tolerance and criterion data. The dyadic ledger $D$ supplies the radius cells consumed by the regular readback, and $Q$ records the Cauchy criterion checks for the same retained family.

The cut ledger $L$ then exposes the Dedekind-style lower and upper rational tests generated by that family. Since $L$ is downstream of $S,R,D,Q$, it cannot select a host limit or quotient stream representative.

Finally $A$ seals only this displayed route, while $H,C,P,N$ preserve, replay, source, and name the same finite packet. Therefore the handoff exports the eta route and none of the excluded classical completeness principles.
\end{proof}

\closureat{DedekindEtaCompletionUp}{seedStr}

\begin{closurestatus}{\DedekindEtaCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-eta-completion-carrier}, \autoref{thm:dedekind-eta-completion-namecert-obligations}, and \autoref{thm:dedekind-eta-completion-l10-handoff} seed the finite eta-completion route over StreamName, RegSeqRat, DyadicRatCore, CauchyCriterionEquivalence, Real, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected host limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, window exactness, dyadic tolerance exactness, Cauchy criterion compatibility, cut locatedness, real-seal handoff, classifier transport, replay, and non-escape for BEDC.Derived.DedekindEtaCompletionUp.}
  \constructivestory{A $\DedekindEtaCompletionUp$ packet is generated from StreamName finite windows, RegSeqRat readbacks, DyadicRatCore tolerance rows, a CauchyCriterionEquivalence comparison row, a located cut ledger, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
