\chapter{A Concrete Naming Certificate for $\CompactUniformPullbackUp$}
\label{ch:concrete-instances-compact-uniform-pullback-namecert}
\origin{human}

Following Bishop and Bridges on compact-uniform continuity, the $\CompactUniformPullbackUp$ packet realizes the compact-uniform routes of \autoref{ch:visions-compact-uniform-continuity} as a finite pullback carrier joining compact-net data, pointwise-modulus rows, dyadic tolerances, regular rational readbacks, and the terminal real-name seal. It sits after the compact metric carrier of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map surface of \autoref{ch:concrete-instances-continuousmap-namecert}, the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}, the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational sequence route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the recurring compact-uniform handoff without exporting a host modulus selector, quotient point equality, open-cover choice, or ambient Heine--Cantor theorem.

\begin{definition}[Compact uniform pullback carrier]
\label{def:compact-uniform-pullback-carrier}
A $\CompactUniformPullbackUp$ carrier is a finite $\BHist$ packet
$$
U=(K,F,M,D,R,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ row naming the compact source, finite net, located-distance ledger, and coverage witnesses used by the pullback.
\item $F$ is the $\ContinuousMapUp$ row naming the graph, pointwise-modulus ledger, source metric, and target metric.
\item $M$ is the $\UniformModulusUp$ consumer row requested by downstream compact-uniform arguments.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row. It records dyadic tolerances, half-radius budgets, and finite lower-bound comparisons used in the compact-net fold.
\item $R$ is the $\RegSeqRatUp$ readback route for the rational precision histories produced by the fold.
\item $E$ is the $\RealUp$ seal row that exposes the final precision and target estimate only after the dyadic and regular-rational rows are accepted.
\item $T$ is the pullback ledger. It records how a target tolerance request is pulled back through $F$, through compact finite-net rows in $K$, through the dyadic budget in $D$, through the regular-rational readback in $R$, and into the uniform-modulus consumer row $M$.
\item $H$ records componentwise $\hsame$ transport for compact metric, continuous map, uniform-modulus, dyadic tolerance, regular readback, real seal, pullback, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from every compact-uniform request through $K,F,M,D,R,E,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CompactUniformPullbackUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactUniformPullbackUp}$ row.
\end{enumerate}
The classifier compares accepted pullback packets only through these finite rows. It has no coordinate for a host modulus selector, quotient point equality, open-cover choice, selected Lebesgue number, or ambient compactness theorem.
\end{definition}
\leanchecked{BEDC.Derived.CompactUniformPullbackUp.CompactUniformPullbackTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Compact uniform pullback NameCert obligations]
\label{thm:compact-uniform-pullback-namecert-obligations}
For every accepted $\CompactUniformPullbackUp$ carrier
$$
U=(K,F,M,D,R,E,T,H,C,P,N),
$$
the local $\NameCert_{\CompactUniformPullbackUp}$ surface consists exactly of compact finite-net admission through $K$, continuous-map pointwise-modulus admission through $F$, uniform-modulus consumer exposure through $M$, dyadic tolerance and lower-bound routing through $D$, regular-rational readback through $R$, real sealing through $E$, pullback ledger visibility through $T$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-uniform-pullback-carrier}. The source rows are $K,F,M$, the arithmetic and seal rows are $D,R,E$, the pullback row is $T$, and the structural rows are $H,C,P,N$.

The finite-net obligation is read through $K$, while pointwise modulus rows are read through $F$. The pullback ledger $T$ is the only row that is allowed to combine those data into a tolerance-only request for $M$.

The arithmetic handoff is also explicit. Dyadic tolerance and lower-bound comparisons stay in $D$, regular-rational readback stays in $R$, and the final real estimate is exposed only through $E$.

Transport, replay, provenance, and local naming preserve this route. Because the carrier has no coordinate for a selected modulus, quotient point equality, open-cover choice, selected Lebesgue number, or host compactness theorem, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Compact uniform pullback modulus handoff]
\label{thm:compact-uniform-pullback-modulus-handoff}
Every downstream read of an accepted $\CompactUniformPullbackUp$ packet factors through
$$
K,F,D,R,E,T \longmapsto M .
$$
Thus a compact-uniform consumer receives a $\UniformModulusUp$ row only after the compact finite-net data, pointwise-modulus rows, dyadic tolerance budget, regular-rational readback, real seal, and pullback ledger have all been displayed inside the same finite carrier.
\end{theorem}
\begin{proof}
Begin with a downstream target tolerance request. The continuous-map row $F$ supplies the pointwise-modulus rows inspected at compact-net centers, and the compact metric row $K$ supplies the finite net and coverage witnesses used to choose those centers inside $\BHist$.

The dyadic tolerance row $D$ performs the finite lower-bound comparisons. Its output is read through $R$ as a regular rational precision history and then through $E$ as a real-sealed estimate.

The pullback ledger $T$ records that these rows are consumed in this order before the consumer row $M$ is exposed. Componentwise transport and replay can only preserve the displayed route, so no host modulus selector or open-cover choice is exported.
\end{proof}

\falsifiablePrediction{Every accepted $\CompactUniformPullbackUp$ modulus read factors through a CompactMetricUp finite-net row, a ContinuousMapUp pointwise-modulus row, a UniformModulusUp consumer row, DyadicRatCoreUp tolerance arithmetic, RegSeqRatUp readback, a RealUp seal, a pullback ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}

\independenceWitness{compactmetric, continuousmap, uniformmodulus, dyadicratcore, regseqrat, real: $\CompactUniformPullbackUp$ is not bijective to any listed sibling because it jointly binds compact finite-net coverage, pointwise-modulus rows, dyadic tolerance budgets, regular rational readback, real sealing, a downstream uniform-modulus consumer, transport, replay, provenance, and local naming in one certificate.}

\closureat{CompactUniformPullbackUp}{seedStr}

\begin{closurestatus}{\CompactUniformPullbackUp}
  \constructivestory{A $\CompactUniformPullbackUp$ packet is generated from CompactMetricUp finite-net rows, ContinuousMapUp pointwise-modulus rows, a UniformModulusUp consumer row, DyadicRatCoreUp tolerance arithmetic, RegSeqRatUp readback, a RealUp seal, a compact-uniform pullback ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-pullback-carrier}, \autoref{thm:compact-uniform-pullback-namecert-obligations}, and \autoref{thm:compact-uniform-pullback-modulus-handoff} seed the finite compact-net, pointwise-modulus, dyadic-tolerance, regular-readback, and real-seal handoff to uniform-modulus consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host modulus selection, quotient point equality, open-cover choice, selected Lebesgue numbers, ambient Heine--Cantor theorems, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked compact finite-net admission, pointwise-modulus admission, dyadic tolerance exactness, regular readback, real sealing, pullback ledger visibility, uniform-modulus export, replay stability, provenance exhaustion, and local naming for BEDC.Derived.CompactUniformPullbackUp.}
\end{closurestatus}
