\chapter{A Concrete Naming Certificate for $\CaristiFixedPointUp$}
\label{ch:concrete-instances-caristi-fixed-point-namecert}
\origin{human}

Following Caristi's fixed point theorem and the Ekeland complete-metric descent route, the $\CaristiFixedPointUp$ packet records the finite surface by which a self-map satisfying a potential-decrease inequality reaches a seal-facing fixed endpoint. It sits beside the Banach fixed-point packet of \autoref{ch:concrete-instances-banach-fixed-point-namecert}, the stability handoff of \autoref{ch:concrete-instances-banach-fixed-point-stability-namecert}, and the variational descent ledger of \autoref{ch:concrete-instances-ekeland-variational-principle-namecert}. The packet names a complete-metric fixed-point certificate over one displayed potential and one displayed self-map; it is not a host minimizer theorem, a choice-selected descent sequence, quotient equality of points, or ambient $\RealUp$ completeness.

\begin{definition}[Caristi fixed point carrier]
\label{def:caristi-fixed-point-carrier}
A $\CaristiFixedPointUp$ carrier is a finite $\BHist$ packet
$$
C=(X,d,\phi,T,E,B,R,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\CompleteMetricUp$ domain row, naming the metric carrier and its complete-metric handoff surface.
\item $d$ is the distance row used for all comparisons between a point and its image under $T$.
\item $\phi$ is the lower-semicontinuous potential row, read through $\LowerSemicontinuousUp$ and a regular-rational value ledger.
\item $T$ is the self-map row whose graph is inspected only through the displayed $\Cont$ route.
\item $E$ is the Caristi descent inequality row, recording the finite comparison $d(x,T x)\leq \phi(x)-\phi(Tx)$ for every admitted probe row.
\item $B$ is the Ekeland handoff row, exposing the variational descent route that turns the potential inequality into a terminal fixedness boundary.
\item $R$ is the $\RegSeqRatUp$ and $\RealUp$ endpoint seal, used only after the complete-metric descent row has been consumed.
\item $H$ records componentwise $\hsame$ transport for the domain, distance, potential, self-map, descent, Ekeland handoff, endpoint seal, replay, provenance, and local naming rows.
\item $Q$ records displayed $\Cont$ replay from any fixed-point read through $X,d,\phi,T,E,B,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\CaristiFixedPointUp$, $\CompleteMetricUp$, $\MetricSpaceUp$, $\LowerSemicontinuousUp$, $\EkelandVariationalPrincipleUp$, $\BanachFixedPointUp$, $\PicardIterationUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CaristiFixedPointUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,d,\phi,T,E,B,R,H,Q,P,N$. It has no coordinate for a host-selected minimizer, arbitrary choice sequence, quotient point equality, global contraction theorem, or ambient completeness beyond the displayed $\CompleteMetricUp$ row.
\end{definition}

\begin{theorem}[Caristi fixed point NameCert obligations]
\label{thm:caristi-fixed-point-namecert-obligations}
For every accepted $\CaristiFixedPointUp$ carrier
$$
C=(X,d,\phi,T,E,B,R,H,Q,P,N),
$$
the local $\NameCert_{\CaristiFixedPointUp}$ surface consists exactly of carrier admission for the complete-metric row, distance row, lower-semicontinuous potential, self-map row, Caristi descent inequality, Ekeland handoff, endpoint seal, transport, replay, provenance, and local naming. The obligation surface also records the comparison boundary with $\BanachFixedPointUp$ and $\PicardIterationUp$: Banach supplies contraction-orbit fixedness, while this packet supplies potential-descent fixedness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:caristi-fixed-point-carrier}. Its analytic rows are exactly $X,d,\phi,T,E,B,R$, and its structural rows are exactly $H,Q,P,N$.

The descent inequality is local to the displayed self-map. The row $E$ reads $d$, $\phi$, and $T$ together, so a consumer cannot detach the distance comparison from the lower-semicontinuous potential ledger.

The fixed-point endpoint is downstream from complete-metric descent. The row $B$ sends the Caristi inequality into the Ekeland variational handoff, and $R$ seals only the resulting regular-rational and real endpoint boundary.

Finally the Banach/Picard comparison is only a boundary row. The provenance records the neighbouring fixed-point route, but the carrier has no contraction constant or Picard-orbit coordinate from which a Banach proof could be read. Hence the displayed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Caristi fixed point Ekeland handoff]
\label{thm:caristi-fixed-point-ekeland-handoff}
Every accepted $\CaristiFixedPointUp$ packet factors its descent read through the finite route
$$
\CompleteMetricUp,\LowerSemicontinuousUp,\EkelandVariationalPrincipleUp
\longmapsto
E,B,R,H,Q,P,N .
$$
The Ekeland handoff consumes the displayed potential-decrease inequality and returns only a certificate-local endpoint boundary. It does not produce a host minimizer, selected descent sequence, quotient equality of points, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $C=(X,d,\phi,T,E,B,R,H,Q,P,N)$. The complete-metric row $X$ and distance row $d$ provide the only metric input available to the descent route.

The lower-semicontinuous row $\phi$ and inequality row $E$ then form the Caristi descent datum. A consumer must read $T$ through the same route, because $E$ compares a point with its displayed image under $T$.

Apply the Ekeland handoff row $B$. It repacks the potential-decrease datum as the finite variational descent ledger named by $\EkelandVariationalPrincipleUp$, and it leaves the endpoint seal to $R$.

The transport, replay, provenance, and local name preserve this order. Since the carrier has no selector row for a host minimizer or arbitrary descent sequence, the handoff exports only the stated certificate-local endpoint boundary.
\end{proof}

\begin{theorem}[Caristi fixed point endpoint fixedness and non-escape]
\label{thm:caristi-fixed-point-endpoint-fixedness-nonescape}
For an accepted $\CaristiFixedPointUp$ carrier, the endpoint row $R$ is classifier-fixed under the displayed self-map row $T$ after the Caristi descent inequality $E$ and Ekeland handoff $B$ have been consumed. Every endpoint read factors through
$$
X,d,\phi,T,E,B,R,H,Q,P,N,
$$
and no consumer may read host fixed-point equality, selected limits, quotient point equality, global contraction soundness, or ambient $\RealUp$ completeness from the packet.
\end{theorem}
\begin{proof}
Read the endpoint row through the carrier. The row $R$ is introduced only after the complete-metric, potential, self-map, inequality, and Ekeland handoff rows have been displayed.

The fixedness assertion is classifier-internal. Applying $T$ at the endpoint route is allowed only through $Q$, and the comparison back to $R$ is transported by $H$ inside the same local $\NameCert$ surface.

The non-escape boundary follows from the absence of additional coordinates. There is no row for a host equality of points, a selected limiting sequence, quotient equality, a contraction constant, or ambient real-completeness theorem. Thus every endpoint fixedness read remains inside $X,d,\phi,T,E,B,R,H,Q,P,N$.
\end{proof}

\falsifiablePrediction{Every accepted $\CaristiFixedPointUp$ endpoint read factors through a CompleteMetricUp row, a lower-semicontinuous potential row, a displayed Caristi descent inequality, an EkelandVariationalPrincipleUp handoff, a RegSeqRatUp and RealUp endpoint seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}

\independenceWitness{banachfixedpoint, banach-fixed-point-stability, ekeland-variational-principle, picard-iteration, complete-metric: $\CaristiFixedPointUp$ is not bijective to any listed sibling because it jointly stores complete-metric descent, lower-semicontinuous potential, self-map graph, Caristi inequality, Ekeland handoff, Banach/Picard comparison boundary, endpoint sealing, transport, replay, provenance, and local naming in one certificate.}

\closureat{CaristiFixedPointUp}{seedStr}

\begin{closurestatus}{\CaristiFixedPointUp}
  \constructivestory{A $\CaristiFixedPointUp$ packet is generated from a complete-metric row, distance row, lower-semicontinuous potential row, self-map row, Caristi descent inequality, Ekeland handoff, Banach/Picard comparison boundary, RegSeqRat and Real endpoint seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:caristi-fixed-point-carrier}, \autoref{thm:caristi-fixed-point-namecert-obligations}, \autoref{thm:caristi-fixed-point-ekeland-handoff}, and \autoref{thm:caristi-fixed-point-endpoint-fixedness-nonescape} seed the complete-metric potential-descent fixed-point packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host fixed-point equality, selected minimizers, selected descent sequences, quotient point equality, global contraction soundness, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, lower-semicontinuous potential readback, Caristi inequality exactness, Ekeland handoff, endpoint fixedness, Banach/Picard boundary confinement, transport, replay, provenance, and local naming for BEDC.Derived.CaristiFixedPointUp.}
\end{closurestatus}
