\chapter{A Concrete Naming Certificate for $\SchwartzSpaceUp$}
\label{ch:concrete-instances-schwartz-space-namecert}
\origin{human}

Following Schwartz and Treves on test-function spaces, the $\SchwartzSpaceUp$ packet records the finite locally convex carrier surface behind rapidly decreasing smooth test functions. It sits beside the complete locally convex interface of \autoref{ch:concrete-instances-frechet-space-namecert}, the finite family-seminorm route of \autoref{ch:concrete-instances-seminormed-space-namecert}, the pointwise test-function carrier of \autoref{ch:concrete-instances-schwartz-function-namecert}, and the derivative observation route of \autoref{ch:concrete-instances-weak-derivative-namecert}. The packet gives Fourier, tempered-distribution, weak-derivative, and PDE-facing consumers a displayed test-function-space surface without importing a host topological vector space, quotient function equality, unrestricted seminorm enumeration, selected representatives, or classical completeness.

\begin{definition}[SchwartzSpace carrier]
\label{def:schwartz-space-carrier}
A $\SchwartzSpaceUp$ carrier is a finite $\BHist$ packet
$$
S=(F,V,I,G,D,R,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FrechetSpaceUp$ source row, exposing complete metrizability and locally convex handoff only through the displayed Frechet carrier.
\item $V$ is the $\SeminormedSpaceUp$ finite-family row, naming the seminorm labels used by the Schwartz test-function space read.
\item $I$ is the $\SchwartzFunctionUp$ test-function row, recording the accepted rapidly decreasing smooth windows inspected by the packet.
\item $G$ is the polynomial-growth and rapid-decay ledger. It binds each displayed seminorm index to a derivative order, a polynomial weight, and the real-valued budget read used to test decay.
\item $D$ is the $\WeakDerivativeUp$ stability row, recording derivative-window shifts and sign conventions that remain inside the same Schwartz test-function-space surface.
\item $R$ is the $\RealUp$ scalar readback row used by seminorm values, decay budgets, and completion-facing estimates.
\item $T$ is the completion and distribution nonescape row. It permits Frechet and tempered-distribution consumers to read the displayed test-function-space boundary only after $F,V,I,G,D,R$ have been exposed.
\item $H$ records componentwise $\hsame$ transport for Frechet, seminorm-family, test-function, rapid-decay, derivative, Real, nonescape, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from every test-function-space request through $F,V,I,G,D,R,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\SchwartzSpaceUp$, $\FrechetSpaceUp$, $\SeminormedSpaceUp$, $\SchwartzFunctionUp$, $\WeakDerivativeUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SchwartzSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host Schwartz topology, a quotient of functions, an unrestricted seminorm family, a selected completion point, a distribution dual, nuclearity, Fourier inversion, or classical choice.
\end{definition}

\begin{theorem}[SchwartzSpace NameCert obligations]
\label{thm:schwartz-space-namecert-obligations}
For every accepted $\SchwartzSpaceUp$ carrier
$$
S=(F,V,I,G,D,R,T,H,C,P,N),
$$
the local $\NameCert_{\SchwartzSpaceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed Frechet-space, seminorm-family, Schwartz-function, rapid-decay, weak-derivative, Real, nonescape, transport, replay, provenance, and local naming rows;
\item seminorm growth routing, requiring every seminorm read to choose a displayed finite-family row in $V$ and a polynomial-growth budget in $G$ before a Real value can be consumed from $R$;
\item rapid-decay test-function closure, requiring every accepted test window from $I$ to satisfy the displayed derivative-order and polynomial-weight ledger in $G$;
\item derivative-row stability, requiring weak-derivative shifts to pass through $D$ and return to the same $I,G,R$ surface rather than to host smooth-function equality;
\item completion and distribution nonescape, requiring $T$ to mediate every Frechet, completion-facing, Fourier-facing, tempered-distribution, or PDE-facing read after $F,V,I,G,D,R$ have been displayed.
\end{enumerate}
No $\SchwartzSpaceUp$ obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:schwartz-space-carrier}. The analytic rows are exactly $F,V,I,G,D,R,T$, and the structural rows are exactly $H,C,P,N$.

Seminorm growth routing is forced by the order of the carrier. A consumer first reads the finite family row $V$, then the derivative and polynomial-weight budget in $G$, and only then may read a Real scalar estimate through $R$.

Rapid-decay closure and derivative stability are the two test-function-space checks. The row $I$ supplies accepted Schwartz test windows, while $G$ records their rapid-decay budgets and $D$ records the weak-derivative shifts that stay inside the same displayed surface.

Finally $T$ is a boundary row rather than an additional topological object. It lets Frechet, completion-facing, Fourier-facing, tempered-distribution, and PDE consumers replay the same rows without receiving a host Schwartz topology, quotient function equality, selected completion point, distribution dual, nuclearity, inversion theorem, or choice principle. Thus the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[SchwartzSpace functional-analysis handoff]
\label{thm:schwartz-space-functional-analysis-handoff}
Every accepted $\SchwartzSpaceUp$ packet exported to a Frechet, Fourier, tempered-distribution, weak-derivative, or PDE-facing consumer factors through
$$
\FrechetSpaceUp,\ \SeminormedSpaceUp,\ \SchwartzFunctionUp,\ \WeakDerivativeUp,\ \RealUp
\longmapsto
F,V,I,G,D,R,T,H,C,P,N .
$$
The exported object is a finite test-function-space NameCert surface with displayed seminorm growth budgets and derivative stability. It is not a host locally convex function space, an unrestricted seminorm enumeration, a selected completion, a dual-space quotient, or a classical distribution theorem.
\end{theorem}
\begin{proof}
Open the accepted carrier using \autoref{def:schwartz-space-carrier}. Any functional-analysis request must first choose one of the displayed source rows $F,V,I,D,R$ and then pass through the growth ledger $G$.

Use \autoref{thm:schwartz-space-namecert-obligations}. The seminorm and rapid-decay obligations keep polynomial weights and derivative orders attached to finite displayed rows, while the derivative-row obligation prevents a consumer from replacing weak-derivative stability by host smooth-function equality.

The nonescape row $T$ is then the only export boundary. Transport, replay, provenance, and local naming through $H,C,P,N$ preserve the same finite route for every downstream consumer. Since no excluded host object is a carrier coordinate, the displayed route is the whole handoff surface.
\end{proof}

\falsifiablePrediction{An accepted $\SchwartzSpaceUp$ consumer that reaches a Frechet, Fourier, tempered-distribution, weak-derivative, or PDE-facing read without first exposing $F,V,I,G,D,R,T,H,C,P,N$ refutes the carrier surface of \autoref{def:schwartz-space-carrier}.}

\independenceWitness{frechet-space, seminormed-space, schwartz-function, weak-derivative, real: no listed sibling is bijective to $\SchwartzSpaceUp$ because this packet jointly binds complete locally convex source rows, finite seminorm-family exposure, rapid-decay test-function windows, derivative stability, Real budget readback, completion and distribution nonescape, transport, replay, provenance, and local naming in one test-function-space carrier.}

\closureat{SchwartzSpaceUp}{seedStr}

\begin{closurestatus}{\SchwartzSpaceUp}
  \constructivestory{A $\SchwartzSpaceUp$ packet is generated from a FrechetSpace row, a finite SeminormedSpace family row, SchwartzFunction test windows, rapid-decay and polynomial-growth ledgers, WeakDerivative stability rows, Real scalar readback, completion and distribution nonescape, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:schwartz-space-carrier}, \autoref{thm:schwartz-space-namecert-obligations}, and \autoref{thm:schwartz-space-functional-analysis-handoff} seed the finite locally convex test-function-space surface consumed by Frechet, Fourier, tempered-distribution, weak-derivative, and PDE-facing packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host Schwartz topology, quotient function equality, unrestricted seminorm enumeration, selected completion, distribution duality, nuclearity, Fourier inversion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, seminorm growth routing, rapid-decay test-function closure, derivative-row stability, completion and distribution nonescape, transport, replay, provenance, and local naming for BEDC.Derived.SchwartzSpaceUp.}
\end{closurestatus}
