\chapter{A Concrete Naming Certificate for $\RHRouteHaltingBoundaryUp$}
\label{ch:concrete-instances-rh-route-halting-boundary-namecert}
\origin{human}

Following the classical separation between the Riemann Hypothesis as a fixed proposition and proof search as a metamathematical process, the $\RHRouteHaltingBoundaryUp$ packet records the finite BEDC surface of the route-closure boundary described in \autoref{ch:visions-rh-route-halting-boundary}. It sits over the RH condition-chain rows of that vision chapter, the halting distinction traces of \autoref{ch:concrete-instances-haltingdistinctiontrace-namecert}, the halting obstruction of \autoref{ch:concrete-instances-haltingobstruction-namecert}, the proof witness chain surface of \autoref{ch:concrete-instances-proofwitnesschain-namecert}, and the zeta-zero witness boundary of \autoref{ch:concrete-instances-zeta-zeros-namecert}. The packet names route, grounding-rank, decider-refusal, and NameCert rows; it does not decide $\mathsf{RH}$, prove $\mathsf{RH}$, refute $\mathsf{RH}$, or assert independence for any chosen fragment.

\begin{definition}[RH-route halting boundary carrier]
\label{def:rh-route-halting-boundary-carrier}
An $\RHRouteHaltingBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(R,G,D,F,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the RH-route row, recording the displayed condition chain, rule tower, proof-output program, or route family being inspected.
\item $G$ is the grounding-rank row, recording whether the inspected route has a displayed finite rank and, when it does, the finite top certificate and transports back to $\mathsf{RH}$.
\item $D$ is the decider-refusal row, recording that a proposed global or sufficiently expressive RH-route closure decider is a halting-boundary request rather than an internal BEDC classifier.
\item $F$ is the fixed-statement row separating the proposition $\mathsf{RH}$ from route-search totality and from global proof-search classification.
\item $Z$ is the zeta-zero witness interface row, exposing the critical-strip and critical-line witnesses that a genuine RH proof or counterexample datum would have to consume.
\item $H$ records componentwise $\hsame$ transport for route, grounding-rank, refusal, fixed-statement, zeta-witness, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from route inspection through $R,G,D,F,Z,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RHRouteHaltingBoundaryUp$, $\HaltingDistinctionTraceUp$, $\HaltingObstructionUp$, $\ProofWitnessChainUp$, $\ZetaZerosUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RHRouteHaltingBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,G,D,F,Z,H,C,P,N$. It has no coordinate for an RH proof, an RH counterexample, an RH-specific independence theorem, a global theorem-route closure decider, a proof-search oracle, or an unmarked halting predicate.
\end{definition}

\begin{theorem}[RH-route halting boundary NameCert obligations]
\label{thm:rh-route-halting-boundary-namecert-obligations}
For every accepted $\RHRouteHaltingBoundaryUp$ carrier $B=(R,G,D,F,Z,H,C,P,N)$, the local $\NameCert_{\RHRouteHaltingBoundaryUp}$ surface consists exactly of carrier admission, route-row exposure, grounding-rank exactness, decider-refusal exactness, fixed-RH-statement separation, zeta-witness interface exposure, componentwise transport, displayed replay, package provenance, and local naming. Every decision-facing read must expose
$$
R,G,D,F,Z \longrightarrow H,C,P,N .
$$
The packet distinguishes RH truth from route-closure decidability: it can record finite grounded routes and reject global closure deciders, but it does not provide $\Phi:\mathsf{RH}$, a counterexample datum, or a fragment-specific independence theorem.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:rh-route-halting-boundary-carrier}. The route row $R$ names the inspected RH-directed condition chain, rule tower, or proof-output route, while $G$ records the displayed grounding-rank information attached to that route.

The refusal row $D$ is read separately from the fixed-statement row $F$. Thus the packet can reject a global or expressive route-closure decider as a halting-boundary request without changing the fixed proposition $\mathsf{RH}$.

The zeta-witness interface $Z$ records what a genuine proof or counterexample datum would have to consume. It does not itself supply the total witness function, a counterexample point, or an independence theorem.

The structural rows $H,C,P,N$ transport, replay, source, and name only the displayed route, rank, refusal, fixed-statement, and zeta-interface rows. Since no proof oracle, route oracle, halting predicate, counterexample, or independence theorem occurs among the coordinates, the listed obligations exhaust the finite NameCert surface.
\end{proof}

\begin{theorem}[RH route boundary nondecision]
\label{thm:rh-route-halting-boundary-nondecision}
Every accepted $\RHRouteHaltingBoundaryUp$ packet separates three reads: the fixed $\mathsf{RH}$ statement row, the finite route or grounding-rank row, and the decider-refusal row. Consequently a consumer may use the packet to identify a finite grounded route or to reject an expressive route-closure decider, but no consumer can read an RH truth value, RH refutation, or independence result from the packet alone.
\end{theorem}
\begin{proof}
Project the carrier $B=(R,G,D,F,Z,H,C,P,N)$. The row $F$ names the fixed statement, while $R$ and $G$ name route and grounding-rank data.

The row $D$ records the halting-boundary refusal for global or sufficiently expressive route deciders. This refusal is a statement about the classifier request, not a proof or refutation of the fixed proposition.

The row $Z$ exposes the zeta-zero witness interface required by an actual decision datum. Because no coordinate supplies such a datum, transport and replay through $H,C$ can preserve only the boundary information already displayed.

Package provenance and local naming through $P,N$ do not add a truth-value coordinate. Therefore the packet is a finite halting-boundary NameCert surface, not an RH decision artifact.
\end{proof}

\closureat{RHRouteHaltingBoundaryUp}{seedStr}

\begin{closurestatus}{\RHRouteHaltingBoundaryUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rh-route-halting-boundary-carrier}, \autoref{thm:rh-route-halting-boundary-namecert-obligations}, and \autoref{thm:rh-route-halting-boundary-nondecision} seed the finite route, grounding-rank, decider-refusal, fixed-statement, zeta-interface, transport, replay, provenance, and local naming surface for the RH route halting boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not prove RH, refute RH, establish RH independence over any fragment, provide a global theorem-route closure decider, admit a proof-search oracle, close halting, supply Lean verification, or provide a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, route-row exposure, grounding-rank exactness, decider-refusal exactness, fixed-statement separation, zeta-witness interface exposure, transport, replay, provenance, and local naming for BEDC.Derived.RHRouteHaltingBoundaryUp.}
  \constructivestory{An $\RHRouteHaltingBoundaryUp$ packet is generated from RH route rows, grounding-rank rows, decider-refusal rows, fixed-RH-statement rows, zeta-witness interface rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
