\chapter{A Concrete Naming Certificate for $\FiniteObservationReflectionUp$}
\label{ch:concrete-instances-finite-observation-reflection-namecert}
\origin{ai}

The $\FiniteObservationReflectionUp$ packet realizes the finite observation trace and open prediction horizon of \autoref{sec:observation-and-reflection} as one NameCert surface. It sits beside $\ObservationReflectionPacketUp$ of \autoref{ch:concrete-instances-observationreflectionpacket-namecert}, the finite window interface of \autoref{ch:concrete-instances-finite-observation-interface-namecert}, the reflective inquiry carrier of \autoref{ch:concrete-instances-reflective-inquiry-namecert}, and the open reflection boundary of \autoref{ch:concrete-instances-reflection-gap-boundary-namecert}. Those siblings expose observation roles, windows, paired inquiry, or gap boundaries separately; this packet binds source, finite observation trace, signature, classifier, package, ledger, and open-continuation rows as one finite observation-reflection certificate.

\begin{definition}[Finite observation-reflection carrier]
\label{def:finite-observation-reflection-carrier}
A $\FiniteObservationReflectionUp$ carrier is a finite $\BHist$ packet
$$
F=(S,O,G,C,P,L,E,T,R,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source row naming the reality-facing or formal-reflection source under inspection.
\item $O$ is the finite observation-trace row, read through a displayed $\FiniteObservationInterfaceUp$ window.
\item $G$ is the observed-signature row extracted from the finite trace.
\item $C$ is the classifier row comparing the source claim with the observed signature.
\item $P$ is the package row recording the model, law, or inquiry certificate that is being tested against the trace.
\item $L$ is the ledger row for approximation budgets, rejected fits, and unresolved residue.
\item $E$ is the open-continuation row preserving the prediction horizon beyond the displayed trace.
\item $T$ records componentwise $\hsame$ transport for $S,O,G,C,P,L,E$.
\item $R$ records displayed $\Cont$ replay from source and trace through signature, classifier, package, ledger, and open continuation.
\item $N$ is the local $\NameCert_{\FiniteObservationReflectionUp}$ row.
\end{enumerate}
The carrier contains no coordinate for a final physical oracle, a closed prediction horizon, source-domain identity, host validation, quotient trace equality, or an unbounded observation schedule.
\end{definition}

\begin{theorem}[Finite observation-reflection NameCert obligations]
\label{thm:finite-observation-reflection-namecert-obligations}
For every accepted $\FiniteObservationReflectionUp$ carrier $F=(S,O,G,C,P,L,E,T,R,N)$, the local $\NameCert_{\FiniteObservationReflectionUp}$ surface consists exactly of carrier admission, source exposure through $S$, finite observation-trace exposure through $O$, observed-signature exposure through $G$, classifier exposure through $C$, package exposure through $P$, ledger exposure through $L$, open-continuation exposure through $E$, componentwise transport through $T$, displayed replay through $R$, and local naming through $N$.

These obligations bind the observation-reflection route
$$
\ObservationReflectionPacketUp \longmapsto \FiniteObservationInterfaceUp \longmapsto \ReflectiveInquiryUp \longmapsto \ReflectionGapBoundaryUp
$$
without adding final truth, closed prediction, source identity, host validation, quotient trace equality, or an unbounded schedule.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-observation-reflection-carrier}. The source and observation rows $S,O$ are displayed separately, so the packet can relate source claims to traces without identifying them.

The signature, classifier, and package rows $G,C,P$ supply the finite comparison surface. They read the observed trace and the tested certificate as rows of the packet rather than as external host judgments.

The ledger and open-continuation rows then preserve non-finality. Row $L$ records budgets, rejected fits, and unresolved residue, while $E$ keeps the prediction horizon open beyond the finite trace.

Finally $T,R,N$ transport, replay, and name exactly the same rows. Since no final oracle, closed horizon, source identity, quotient trace, or unbounded schedule is present, the local NameCert surface has precisely the listed obligations.
\end{proof}

\begin{theorem}[Finite observation-reflection open horizon]
\label{thm:finite-observation-reflection-open-horizon}
Let $F=(S,O,G,C,P,L,E,T,R,N)$ be an accepted $\FiniteObservationReflectionUp$ packet. Every consumer that reads an observation-reflection judgment from $F$ must pass through the source row $S$, the finite observation trace $O$, the signature row $G$, the classifier row $C$, the package row $P$, the ledger row $L$, and the open-continuation row $E$.

In particular, the packet can certify a finite source--trace--signature fit while refusing to close the prediction horizon or identify the source with its observations.
\end{theorem}
\begin{proof}
Begin with the trace route. The source row $S$ and finite observation row $O$ are distinct coordinates, and the signature row $G$ is extracted only from the displayed finite trace.

The classifier and package rows $C,P$ then record the tested fit. This fit is ledgered by $L$, which keeps approximation budgets, rejected alternatives, and unresolved residue visible to downstream readers.

The open-continuation row $E$ is read before the local name is exported. Componentwise transport and replay through $T,R$ preserve that order, so a consumer cannot turn a finite observation-reflection packet into a final truth oracle or a closed prediction horizon.
\end{proof}

\falsifiablePrediction{Every accepted $\FiniteObservationReflectionUp$ read exposes source, finite observation trace, signature, classifier, package, ledger, open continuation, transport, replay, and local NameCert rows before exporting an observation-reflection judgment.}

\independenceWitness{observationreflectionpacket, finiteobservationinterface, reflectiveinquiry, reflectiongapboundary: $\FiniteObservationReflectionUp$ is not bijective to any listed sibling because it jointly carries source, finite trace, signature, classifier, package, ledger, and open-continuation rows in one NameCert surface.}

\closureat{FiniteObservationReflectionUp}{seedStr}

\begin{closurestatus}{\FiniteObservationReflectionUp}
  \constructivestory{A $\FiniteObservationReflectionUp$ packet is generated from source, finite observation trace, observed signature, classifier, package, ledger, open continuation, componentwise transport, displayed replay, and local NameCert naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-observation-reflection-carrier}, \autoref{thm:finite-observation-reflection-namecert-obligations}, and \autoref{thm:finite-observation-reflection-open-horizon} seed the finite observation-reflection route and its open prediction horizon.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close final physical truth, final formal truth, source-domain identity, host validation, quotient trace equality, unbounded observation schedules, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked source, observation-trace, signature, classifier, package, ledger, open-continuation, transport, and replay rows for BEDC.Derived.FiniteObservationReflectionUp.}
\end{closurestatus}
