\chapter{A Concrete Naming Certificate for $\ArchimedeanOrderedCauchyCompletionUp$}
\label{ch:concrete-instances-archimedean-ordered-cauchy-completion-namecert}
\origin{human}

Following Bishop--Bridges constructive completion, the $\ArchimedeanOrderedCauchyCompletionUp$ packet records the finite NameCert surface for an Archimedean ordered Cauchy completion built from displayed dyadic rational data. It sits as an L10 real-completion neighbour of the dyadic carrier of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-name interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the constructive order handoff of \autoref{sec:realalgorder-concrete-interface}. The packet binds density, Archimedean order, regular-Cauchy sealing, and RealUp readback in one finite carrier; it does not import quotient completion, selected limits, trichotomy, countable choice, host real equality, or ambient completeness.

\begin{definition}[ArchimedeanOrderedCauchyCompletion carrier]
\label{def:archimedean-ordered-cauchy-completion-carrier}
An $\ArchimedeanOrderedCauchyCompletionUp$ carrier is a finite $\BHist$ packet
$$
A=(D,S,Q,R,O,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ row carrying dyadic rational observations, signed arithmetic, tolerance comparison, and density requests.
\item $S$ is the $\StreamNameUp$ row exposing finite observation windows for completion names.
\item $Q$ is the $\RegSeqRatUp$ row reading regular Cauchy rational sequences through the same dyadic tolerances.
\item $R$ is the $\RealUp$ seal row reached only after $D,S,Q$ have been displayed.
\item $O$ is the $\RealAlgOrderUp$ order-and-apartness handoff row for the sealed real names.
\item $L$ is the Archimedean density ledger: every displayed positive tolerance request is answered by a dyadic row of $D$ before the corresponding stream window and regular-readback row are consumed.
\item $H$ records componentwise $\hsame$ transport for $D,S,Q,R,O,L$.
\item $C$ records displayed $\Cont$ replay of the same completion route.
\item $P$ is the $\Pkg$ provenance over $\ArchimedeanOrderedCauchyCompletionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RealAlgOrderUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ArchimedeanOrderedCauchyCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for a quotient set of Cauchy sequences, a selected representative, a global order decision, countable choice, or a separate completeness oracle.
\end{definition}

\begin{theorem}[ArchimedeanOrderedCauchyCompletion NameCert obligations]
\label{thm:archimedean-ordered-cauchy-completion-namecert-obligations}
For every accepted $\ArchimedeanOrderedCauchyCompletionUp$ carrier $A=(D,S,Q,R,O,L,H,C,P,N)$, the local $\NameCert_{\ArchimedeanOrderedCauchyCompletionUp}$ surface consists exactly of carrier admission for dyadic rational observations, finite stream windows, regular-Cauchy rational readback, terminal real sealing, constructive order and apartness, Archimedean density, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. Every completion-facing read must pass through $D,S,Q,R,O,L,H,C,P,N$, and no obligation may be discharged by quotient completion, host equality of reals, trichotomy, selected limits, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:archimedean-ordered-cauchy-completion-carrier}. The rows $D,S,Q$ form the finite completion spine: dyadic tolerances are displayed first, finite observation windows are then opened, and regular rational readback is admitted only through those windows.

The seal row $R$ is reached after that spine, and the order row $O$ reads the sealed names through the constructive order interface. Thus the order surface is downstream of the same regular-Cauchy route rather than an independent host order predicate.

The density ledger $L$ answers each positive tolerance request with a dyadic row before the stream and readback rows are consumed. Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since these are all carrier coordinates, the excluded quotient, selector, trichotomy, choice, host-equality, and ambient-completeness routes have no entry point.
\end{proof}

\begin{theorem}[ArchimedeanOrderedCauchyCompletion density seal]
\label{thm:archimedean-ordered-cauchy-completion-density-seal}
Every downstream consumer of an accepted $\ArchimedeanOrderedCauchyCompletionUp$ packet receives density and order only through the finite handoff
$$
\DyadicRatCoreUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp \longmapsto \RealAlgOrderUp .
$$
Consequently an Archimedean approximation, an order comparison, or a regular-Cauchy completion read can use only the displayed dyadic tolerance rows, finite windows, regular rational readbacks, RealUp seal, order handoff, transports, continuations, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:archimedean-ordered-cauchy-completion-namecert-obligations}. It forces every completion-facing read through the dyadic row, stream-window row, regular-readback row, real seal, and order row.

The Archimedean density ledger is attached to the same dyadic row. A consumer asking for an approximation at a positive tolerance therefore reads $L$ through $D$ before any stream window, regular rational name, real seal, or order comparison becomes available.

The structural rows $H,C,P,N$ preserve this route under transport and replay. They can expose the handoff as a named packet, but they cannot add a quotient representative, selected limit, trichotomy branch, countable-choice schedule, host equality of real names, or ambient completeness theorem.
\end{proof}

\closureat{ArchimedeanOrderedCauchyCompletionUp}{seedStr}

\begin{closurestatus}{\ArchimedeanOrderedCauchyCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:archimedean-ordered-cauchy-completion-carrier}, \autoref{thm:archimedean-ordered-cauchy-completion-namecert-obligations}, and \autoref{thm:archimedean-ordered-cauchy-completion-density-seal} seed the finite Archimedean ordered Cauchy completion route through DyadicRatCore, StreamName, RegSeqRat, RealUp, RealAlgOrder, density, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected Cauchy representatives, trichotomy, countable choice, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic density, finite-window readback, regular-Cauchy sealing, RealUp handoff, RealAlgOrder order exposure, transport, replay, provenance, local naming, and nonescape for BEDC.Derived.ArchimedeanOrderedCauchyCompletionUp.}
  \constructivestory{An $\ArchimedeanOrderedCauchyCompletionUp$ packet is generated from dyadic rational observations, finite stream windows, regular Cauchy rational readback, a terminal RealUp seal, constructive order and apartness rows, an Archimedean density ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
