\chapter{A Concrete Naming Certificate for $\LegitimateClaimAuditLedgerUp$}
\label{ch:concrete-instances-legitimate-claim-audit-ledger-namecert}
\origin{ai}

The $\LegitimateClaimAuditLedgerUp$ packet realizes the claim-status surface of \autoref{ch:visions-legitimate-claim-audit} as a finite NameCert carrier. It sits beside the kernel witness of \autoref{ch:concrete-instances-kernel-audit-witness-namecert}, the audit gate boundary of \autoref{ch:concrete-instances-auditgateboundary-namecert}, the apophatic naming surface of \autoref{ch:concrete-instances-apophaticname-namecert}, and the corpus-supply distillation packet of \autoref{ch:concrete-instances-corpus-supply-distillation-namecert}. Those siblings audit declarations, local gates, named externality, and source supply separately; this packet binds claim source, admissibility gate, refusal socket, marker provenance, replay, and local naming as one visible ledger.

\begin{definition}[Legitimate-claim audit ledger carrier]
\label{def:legitimate-claim-audit-ledger-carrier}
A $\LegitimateClaimAuditLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(S,G,R,M,K,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the claim-source row, recording the finite expression, subject surface, cited carrier, and supplied evidence route.
\item $G$ is the admissibility-gate row, read through $\AuditGateBoundaryUp$ and recording whether the claim may enter as theorem, condition, route, evidence, non-evidence, meta-row, refusal, gap, or socket.
\item $R$ is the refusal-socket row, recording the named boundary where hidden supply, ungenerated proof content, unmarked corpus material, or external truth pressure is refused.
\item $M$ is the marker-provenance row, recording the paper marker, Lean target name when present, source chapter, and resolution status without asserting a theorem absent kernel acceptance.
\item $K$ is the kernel-audit row, read through $\KernelAuditWitnessUp$ when the claim cites Lean-accepted theorem content.
\item $A$ is the apophatic-name row, read through $\ApophaticNameUp$ when the claim exposes an external dependency position rather than consuming it.
\item $H$ records componentwise $\hsame$ transport for source, gate, refusal socket, marker provenance, kernel audit, apophatic name, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for the same ledger route through $S,G,R,M,K,A,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LegitimateClaimAuditLedgerUp$, $\KernelAuditWitnessUp$, $\AuditGateBoundaryUp$, $\ApophaticNameUp$, $\CorpusSupplyDistillationUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LegitimateClaimAuditLedgerUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,G,R,M,K,A,H,C,P,N$. It has no coordinate for hidden theorem supply, unledgered corpus import, a global truth predicate, host-side proof search, or an unmarked marker resolution.
\end{definition}

\begin{theorem}[Legitimate-claim audit ledger NameCert obligations]
\label{thm:legitimate-claim-audit-ledger-namecert-obligations}
For an accepted $\LegitimateClaimAuditLedgerUp$ carrier
$$
L=(S,G,R,M,K,A,H,C,P,N),
$$
the local $\NameCert_{\LegitimateClaimAuditLedgerUp}$ surface consists exactly of claim-source exposure, admissibility-gate classification, refusal-socket visibility, marker-provenance exactness, kernel-audit handoff, apophatic-name handoff, componentwise transport, displayed replay, provenance, and local naming. No claim-status obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:legitimate-claim-audit-ledger-carrier}. The accepted packet displays the claim source, admissibility gate, refusal socket, marker provenance, kernel audit row, apophatic name row, and structural rows.

The gate row $G$ classifies the finite expression only with the source row $S$ visible. If a requested dependency is not generated by the packet, the refusal socket $R$ and apophatic row $A$ keep that dependency named rather than consumed.

Marker provenance is the row $M$. When the claim cites Lean theorem content, the kernel row $K$ must be read through the same packet; otherwise the marker remains a provenance row rather than a theorem export.

Transport, replay, provenance, and local naming preserve the displayed ledger. Since the carrier has no other coordinate, it cannot import hidden theorem supply, unledgered corpus material, host proof search, or a global truth predicate.
\end{proof}

\begin{theorem}[Legitimate-claim audit ledger nonescape]
\label{thm:legitimate-claim-audit-ledger-nonescape}
Every accepted $\LegitimateClaimAuditLedgerUp$ claim-status read factors through the displayed route
$$
S,G,R,M,K,A,H,C,P,N.
$$
In particular, a claim whose missing dependency is named by $R$ or $A$ cannot be exported as an unconditional theorem row unless a separate kernel-audit or certificate row is displayed in the same ledger route.
\end{theorem}
\begin{proof}
Start from \autoref{thm:legitimate-claim-audit-ledger-namecert-obligations}. A consumer receives source, gate, refusal, marker, kernel, apophatic, transport, replay, provenance, and local naming data as one finite packet.

If a dependency is generated and accepted, the route may read it through the displayed kernel-audit row $K$ or another displayed certificate row at the claim site. If the dependency is ungenerated, the route exposes it through $R$ or $A$.

The rows $H,C,P,N$ preserve and name the same distinction. They do not add a theorem row, select a hidden proof, or turn apophatic naming into internal supply.

Therefore the ledger can classify theorem, condition, route, evidence, non-evidence, meta-row, refusal, gap, and socket statuses, but it cannot promote a named missing dependency to an unconditional theorem.
\end{proof}

The Lean follow-up file \texttt{lean4/BEDC/Derived/LegitimateClaimAuditLedgerUp/TasteGate.lean} must provide explicit $\Nontrivial\ \LegitimateClaimAuditLedgerUp$ and $\FieldFaithful\ \LegitimateClaimAuditLedgerUp$ instances. The field-faithfulness witness must preserve $S,G,R,M,K,A,H,C,P,N$ as distinct rows so claim source, admissibility gate, refusal socket, marker provenance, kernel audit, and apophatic naming cannot collapse.

\falsifiablePrediction{A claim-status packet that omits the refusal socket while consuming ungenerated theorem supply is rejected as a $\LegitimateClaimAuditLedgerUp$ packet, even when it carries a marker-provenance row or an admissibility-gate row.}

\independenceWitness{kernelauditwitness, auditgateboundary, apophaticname, corpussupplydistillation: $\LegitimateClaimAuditLedgerUp$ is not bijective to any listed sibling because it jointly carries claim source, admissibility gate, refusal socket, marker provenance, kernel audit, apophatic naming, transport, replay, provenance, and local NameCert rows.}

\closureat{LegitimateClaimAuditLedgerUp}{seedStr}

\begin{closurestatus}{\LegitimateClaimAuditLedgerUp}
  \constructivestory{A $\LegitimateClaimAuditLedgerUp$ packet is generated from claim source, admissibility gate, refusal socket, marker provenance, kernel audit, apophatic naming, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:legitimate-claim-audit-ledger-carrier}, \autoref{thm:legitimate-claim-audit-ledger-namecert-obligations}, and \autoref{thm:legitimate-claim-audit-ledger-nonescape} seed the finite audit-ledger surface for legitimate claim status.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, a global truth predicate, hidden proof search, kernel soundness, or unledgered corpus admission.}
  \upgradepath{Obligation closure requires checked carrier admission, claim-source exposure, admissibility-gate classification, refusal-socket visibility, marker-provenance exactness, kernel and apophatic handoffs, TasteGate nontriviality, and field faithfulness for $S,G,R,M,K,A,H,C,P,N$.}
\end{closurestatus}
