\chapter{A Concrete Naming Certificate for $\UpperRealEnvelopeUp$}
\label{ch:concrete-instances-upper-real-envelope-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\UpperRealEnvelopeUp$ packet records a one-sided real-envelope surface obtained by reading upper dyadic bounds beside the lower-upper cut boundary of \autoref{ch:concrete-instances-lower-upper-real-cut-namecert}. It keeps the envelope as finite approximation data through \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}, without selecting a completed cut representative or a host supremum.

\begin{definition}[Upper real envelope carrier]
\label{def:upper-real-envelope-carrier}
An $\UpperRealEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(U,L,D,S,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the upper-envelope ledger, recording finite upper dyadic observations and their tolerance budgets.
\item $L$ is the $\LowerUpperRealCutUp$ boundary row, exposing the two-sided located-cut context against which the envelope is read.
\item $D$ is the $\DyadicRatCoreUp$ comparison row, storing endpoints, radii, slack, and decidable dyadic comparisons used by $U$ and $L$.
\item $S$ is the $\StreamNameUp$ finite-window row, scheduling visible envelope queries without selecting an infinite representative.
\item $R$ is the $\RegSeqRatUp$ regular-Cauchy handoff, carrying the same upper-budget reads into regular sequence form.
\item $A$ is the terminal $\RealUp$ admissibility seal, available only downstream of $U,L,D,S,R$.
\item $H$ records componentwise $\hsame$ transport for the envelope ledger, lower-upper boundary, dyadic row, stream window, regular-Cauchy handoff, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for every envelope-facing read through the same tuple $U,L,D,S,R,A,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\UpperRealEnvelopeUp$, $\LowerUpperRealCutUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UpperRealEnvelopeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $U,L,D,S,R,A,H,C,P,N$. It has no coordinate for quotient-cut equality, a chosen Dedekind representative, trichotomy, countable choice, host supremum, or ambient real completeness.
\end{definition}

\begin{theorem}[Upper real envelope NameCert obligations]
\label{thm:upper-real-envelope-namecert-obligations}
For an accepted $\UpperRealEnvelopeUp$ carrier
$$
E=(U,L,D,S,R,A,H,C,P,N),
$$
the local $\NameCert_{\UpperRealEnvelopeUp}$ surface consists exactly of carrier exposure, upper-envelope ledger stability, lower-upper boundary visibility, dyadic tolerance exactness, finite-window scheduling, regular-Cauchy handoff, terminal real-seal nonescape, componentwise transport, displayed replay, provenance, and local naming. No local obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Carrier exposure is projection from \autoref{def:upper-real-envelope-carrier}. The accepted packet displays exactly the upper ledger, lower-upper boundary, dyadic tolerance row, stream window, regular-Cauchy handoff, real seal, and structural rows.

The upper-envelope ledger is read only through $U,D,S,H,C,P,N$. Componentwise transport preserves the displayed dyadic budget, and replay uses the same finite window rather than a hidden stream representative.

The lower-upper boundary is the row $L$. It keeps every envelope read adjacent to the two-sided located-cut surface of \autoref{ch:concrete-instances-lower-upper-real-cut-namecert}, so the upper ledger cannot detach into an isolated host-side bound.

The handoff rows $R$ and $A$ remain downstream of $U,L,D,S$. Since no other coordinate exists, the packet cannot export quotient-cut equality, a selected representative, trichotomy, countable choice, host supremum, or ambient completeness.
\end{proof}

\begin{theorem}[Upper real envelope lower-upper cut boundary]
\label{thm:upper-real-envelope-lower-upper-cut-boundary}
Every $\RealUp$-facing read of an accepted $\UpperRealEnvelopeUp$ packet factors through the displayed route
$$
U,L,D,S,R,A,H,C,P,N
$$
and keeps the $\LowerUpperRealCutUp$ boundary row visible before any regular-Cauchy or terminal real seal can be consumed. Thus the packet supplies one-sided upper approximation evidence beside a lower-upper cut, not a completed real, quotient cut, selected representative, or host supremum.
\end{theorem}
\begin{proof}
Fix an accepted $\UpperRealEnvelopeUp$ carrier. A consumer first reads the upper-envelope ledger $U$ with the dyadic tolerance row $D$ and the stream window $S$.

The lower-upper cut boundary $L$ is displayed in the same packet. This keeps the one-sided upper observations attached to the two-sided located boundary before any Real-facing read is allowed.

The regular-Cauchy handoff $R$ and real seal $A$ sit downstream of $U,L,D,S$. Transport, replay, provenance, and local naming preserve that same finite route.

Because the carrier has no coordinate for a quotient cut, selected representative, host supremum, trichotomy, countable choice, or completeness principle, the route can export only upper-envelope approximation evidence beside the named lower-upper boundary.
\end{proof}

\closureat{UpperRealEnvelopeUp}{seedStr}

\begin{closurestatus}{\UpperRealEnvelopeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:upper-real-envelope-carrier}, \autoref{thm:upper-real-envelope-namecert-obligations}, and \autoref{thm:upper-real-envelope-lower-upper-cut-boundary} seed the finite one-sided upper-envelope surface beside lower-upper cuts and regular-Cauchy real seals.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Dedekind construction of $\RealUp$, quotient-cut equality, selected representative, host supremum, countable choice, trichotomy, or $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier exposure, upper-ledger stability, lower-upper boundary visibility, dyadic exactness, finite-window scheduling, regular-Cauchy handoff, real-seal nonescape, and local naming for BEDC.Derived.UpperRealEnvelopeUp.}
  \constructivestory{An $\UpperRealEnvelopeUp$ packet is generated from an upper-envelope ledger, a LowerUpperRealCut boundary row, a DyadicRatCore tolerance row, a StreamName finite window, a RegSeqRat handoff, a Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
