\chapter{A Concrete Naming Certificate for $\FiniteIntervalCoverUp$}
\label{ch:concrete-instances-finite-interval-cover-namecert}
\origin{human}

Following Bishop and Bridges, finite interval covers are read here as displayed finite data rather than as open-cover prose. The $\FiniteIntervalCoverUp$ packet realizes the finite-cover branch of \autoref{ch:visions-compact-uniform-continuity} beside the located interval surface of \autoref{ch:concrete-instances-locatedinterval-namecert}, the dyadic interval ledger of \autoref{ch:concrete-instances-dyadicinterval-namecert}, the closed bounded interval packet of \autoref{ch:concrete-instances-closedboundedinterval-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. A consumer sees a finite list of interval rows, endpoint and overlap ledgers, coverage witnesses, transport, replay, provenance, and local naming; it does not see a selected subcover, quotient real cover, endpoint convention selector, trichotomy oracle, or ambient real-completeness principle.

\begin{definition}[FiniteIntervalCover carrier]
\label{def:finite-interval-cover-carrier}
A $\FiniteIntervalCoverUp$ carrier is a finite $\BHist$ packet
$$
F=(I,D,B,W,C,R,E,H,K,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $I$ is the finite interval-index row, recording the displayed cover members.
\item $D$ is the $\DyadicIntervalUp$ endpoint row for the cover windows.
\item $B$ is the $\ClosedBoundedIntervalUp$ source row being covered.
\item $W$ is the $\LocatedIntervalUp$ witness row for membership and overlap inspections.
\item $C$ is the finite coverage ledger, recording that every accepted source-window read is captured by one displayed interval row.
\item $R$ is the $\RegSeqRatUp$ readback row for rational endpoint comparisons.
\item $E$ is the terminal $\RealUp$ seal for real-facing endpoint reads.
\item $H$ records componentwise $\hsame$ transport for $I,D,B,W,C,R,E$.
\item $K$ records displayed $\Cont$ replay for index lookup, endpoint comparison, coverage inspection, and Real-seal handoff.
\item $P$ is the $\Pkg$ provenance over $\FiniteIntervalCoverUp$, $\LocatedIntervalUp$, $\DyadicIntervalUp$, $\ClosedBoundedIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteIntervalCoverUp}$ row.
\end{enumerate}
The carrier has no coordinate for a choice-selected refinement, quotient real interval, ambient compactness theorem, trichotomy decision, or hidden endpoint convention.
\end{definition}

\begin{theorem}[FiniteIntervalCover NameCert obligations]
\label{thm:finite-interval-cover-namecert-obligations}
For every accepted $\FiniteIntervalCoverUp$ packet $F=(I,D,B,W,C,R,E,H,K,P,N)$, the local $\NameCert_{\FiniteIntervalCoverUp}$ surface consists exactly of finite index admission, dyadic endpoint exposure, closed-bounded source admission, located interval inspection, finite coverage, regular rational readback, terminal Real sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every cover consumer must read the sibling routes named in \autoref{ch:concrete-instances-locatedinterval-namecert}, \autoref{ch:concrete-instances-dyadicinterval-namecert}, \autoref{ch:concrete-instances-closedboundedinterval-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert} before it treats the cover as a real-facing interval cover.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-interval-cover-carrier}. The rows $I,D,B,W,C$ are the finite cover data: they display the interval indices, the dyadic endpoints, the closed bounded source, located membership and overlap checks, and coverage witnesses.

Read the comparison and seal rows next. The route from $D$ and $W$ to a real-facing endpoint passes through $R$ and then $E$, so a consumer cannot replace finite endpoint comparisons by quotient real equality, a selected representative, or trichotomy.

Finally transport the same rows through $H,K,P,N$. Since the carrier contains no additional coordinate, the listed rows exhaust the local NameCert obligations and force every accepted cover read through the displayed sibling lattice.
\end{proof}

\begin{theorem}[FiniteIntervalCover Real handoff]
\label{thm:finite-interval-cover-real-handoff}
Every $\RealUp$-facing read exported by an accepted $\FiniteIntervalCoverUp$ packet first consumes the finite interval-index row $I$, dyadic endpoint row $D$, closed-bounded source row $B$, located interval row $W$, coverage row $C$, and $\RegSeqRatUp$ comparison row $R$. Only after those rows have been transported through $H$, replayed through $K$, packaged by $P$, and named by $N$ may the terminal Real seal $E$ be exposed to a downstream compactness or uniform-modulus consumer.
\end{theorem}
\begin{proof}
Start with \autoref{thm:finite-interval-cover-namecert-obligations}. It makes the finite index, endpoint, source, locatedness, coverage, regular-rational, and Real-seal rows part of one local NameCert surface.

The real-facing handoff is therefore not a direct map from closed intervals to real endpoints. It must inspect the finite cover member, compare its displayed dyadic endpoints through $R$, and retain the closed-bounded source row $B$ and located interval row $W$ before $E$ is available.

The structural rows then preserve the route. Transport by $H$, replay by $K$, provenance by $P$, and local naming by $N$ keep the same packet visible to compactness and uniform-modulus consumers, while the absence of selected refinements, quotient intervals, trichotomy, and ambient completeness prevents any detached Real read.
\end{proof}

\falsifiablePrediction{An accepted $\FiniteIntervalCoverUp$ read is refuted if a RealUp endpoint seal is exposed without the finite index row, dyadic endpoint row, closed-bounded source row, located interval row, coverage row, RegSeqRat readback, transport, replay, provenance, and local naming rows.}

\independenceWitness{locatedinterval, dyadicinterval, closedboundedinterval, streamname, regseqrat, and real: none is bijective to the finite interval-cover packet because only $\FiniteIntervalCoverUp$ records finite interval indices, coverage witnesses, endpoint comparisons, and the Real handoff in one local NameCert surface.}

\closureat{FiniteIntervalCoverUp}{seedStr}

\begin{closurestatus}{\FiniteIntervalCoverUp}
  \constructivestory{A $\FiniteIntervalCoverUp$ packet is generated from finite interval indices, dyadic endpoint rows, a closed-bounded source row, located interval inspection, finite coverage witnesses, RegSeqRat comparison readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-interval-cover-carrier}, \autoref{thm:finite-interval-cover-namecert-obligations}, and \autoref{thm:finite-interval-cover-real-handoff} seed the finite interval-cover object consumed by compactness and uniform-modulus routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected subcovers, endpoint-convention selectors, trichotomy, quotient real intervals, RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite coverage, dyadic endpoint comparison, located interval inspection, RegSeqRat readback, RealUp handoff, transport, replay, provenance, and local naming for BEDC.Derived.FiniteIntervalCoverUp.}
\end{closurestatus}
