\chapter{A Concrete Naming Certificate for $\HyperbolicFixedPointObstructionUp$}
\label{ch:concrete-instances-hyperbolic-fixed-point-obstruction-namecert}
\origin{ai}

The $\HyperbolicFixedPointObstructionUp$ packet realizes the boundary fixed-point reading of \autoref{sec:hyperbolic-consciousness-fixed-point} as finite NameCert data. It sits beside the UnitDisk, HyperbolicMetric, Denjoy--Wolff boundary-dynamics, hyperbolic observer-expansion, and Busemann-boundary packets: those siblings provide disk coordinates, metric comparison, boundary dynamics, observer-expansion rows, and boundary-level readback, while this packet records the obstruction to treating the apophatic far end as an interior fixed point.

\begin{definition}[Hyperbolic fixed-point obstruction carrier]
\label{def:hyperbolic-fixed-point-obstruction-carrier}
A $\HyperbolicFixedPointObstructionUp$ carrier is a finite $\BHist$ packet
$$
O=(D,M,B,E,U,G,R,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $D$ is the $\UnitDiskUp$ coordinate row for the displayed disk surface;
\item $M$ is the $\HyperbolicMetricUp$ row for disk-distance and boundary comparison reads;
\item $B$ is the Denjoy--Wolff boundary-dynamics row, recording the boundary route rather than an interior fixed point;
\item $E$ is the hyperbolic observer-expansion row, recording the expansion ledger whose far-end reading is being inspected;
\item $U$ is the Busemann-boundary row, exposing boundary-level readback for the far end;
\item $G$ is the obstruction row, refusing an interior fixed-point reading of the apophatic far end;
\item $R$ records refusal of a global disk center, a value fixed point for $\mathsf{T}$, a hidden observer point, and a completed hyperbolic universe;
\item $H$ stores componentwise $\hsame$ transport for disk, metric, boundary dynamics, observer expansion, Busemann boundary, obstruction, refusal, replay, provenance, and local naming rows;
\item $C$ stores displayed $\Cont$ replay for the same route;
\item $P$ is the $\Pkg$ provenance over $\HyperbolicFixedPointObstructionUp$, $\UnitDiskUp$, $\HyperbolicMetricUp$, Denjoy--Wolff boundary dynamics, hyperbolic observer expansion, hyperbolic Busemann boundary, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\HyperbolicFixedPointObstructionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an interior value of $\mathsf{T}$, a global disk center, a hidden Hilbert-space fixed point, or a completed ambient hyperbolic geometry.
\end{definition}

\begin{theorem}[Hyperbolic fixed-point obstruction NameCert obligations]
\label{thm:hyperbolic-fixed-point-obstruction-namecert-obligations}
For the carrier of \autoref{def:hyperbolic-fixed-point-obstruction-carrier}, the local $\NameCert_{\HyperbolicFixedPointObstructionUp}$ surface consists exactly of disk-coordinate admission, hyperbolic-metric admission, boundary-dynamics coverage, observer-expansion coverage, Busemann-boundary readback, obstruction refusal, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier $O=(D,M,B,E,U,G,R,H,C,P,N)$. The rows $D,M,B,E,U$ display the disk, metric, boundary-dynamics, observer-expansion, and boundary-readback data that can be inspected.

The obstruction row $G$ is then the only row that states the fixed-point refusal. It may compare the displayed boundary route with the disk and metric rows, but it cannot introduce an interior coordinate for the far end.

Finally $R,H,C,P,N$ record the forbidden readings, transport the route, replay it, source it, and name it. Since the carrier has no further coordinate, these rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Hyperbolic fixed-point boundary-route obstruction]
\label{thm:hyperbolic-fixed-point-boundary-route-obstruction}
Every accepted $\HyperbolicFixedPointObstructionUp$ packet forces the apophatic far-end reading through the boundary route
$$
D,M,B,E,U,G,R,H,C,P,N .
$$
A consumer may read boundary dynamics, observer expansion, and Busemann-level boundary data, but it cannot convert those rows into an interior disk fixed point, a global center, or a value of $\mathsf{T}$.
\end{theorem}
\begin{proof}
Start with the disk and metric rows. The packet displays $D$ and $M$ only as coordinates and comparisons for the visible disk surface.

Next read the boundary rows. The Denjoy--Wolff-style row $B$, observer-expansion row $E$, and Busemann-boundary row $U$ place the fixedness language at the boundary route, not at an interior point.

The obstruction row $G$ and refusal row $R$ block the forbidden conversions. Transport, replay, provenance, and naming through $H,C,P,N$ preserve the same finite route, so the accepted packet exports a boundary-route obstruction and nothing stronger.
\end{proof}

\falsifiablePrediction{A hyperbolic observer-expansion consumer that obtains an interior disk point for $\mathsf{T}$ without reading the boundary rows $B,E,U,G$ refutes the $\HyperbolicFixedPointObstructionUp$ packet.}

\independenceWitness{unitdisk, hyperbolic-metric, denjoy-wolff-boundary-dynamics, hyperbolic-observer-expansion, hyperbolic-busemann-boundary: the UnitDisk packet supplies disk coordinates without fixed-point refusal, the HyperbolicMetric packet supplies metric comparison without apophatic boundary routing, the Denjoy--Wolff boundary-dynamics packet supplies boundary dynamics without observer-expansion obstruction, the observer-expansion packet supplies expansion rows without Busemann boundary readback, and the Busemann-boundary packet supplies boundary-level readback without the full obstruction carrier. None is bijective to $\HyperbolicFixedPointObstructionUp$.}

\closureat{HyperbolicFixedPointObstructionUp}{seedStr}

\begin{closurestatus}{\HyperbolicFixedPointObstructionUp}
  \constructivestory{A $\HyperbolicFixedPointObstructionUp$ packet is generated from disk, hyperbolic metric, boundary-dynamics, observer-expansion, Busemann-boundary, obstruction, refusal, transport, replay, provenance, and local naming rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-fixed-point-obstruction-carrier}, \autoref{thm:hyperbolic-fixed-point-obstruction-namecert-obligations}, and \autoref{thm:hyperbolic-fixed-point-boundary-route-obstruction} seed the finite boundary-route obstruction to interior fixed-point readings.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a global disk center, an interior value for $\mathsf{T}$, host hyperbolic dynamics, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked disk, metric, boundary-dynamics, observer-expansion, Busemann-boundary, obstruction, and refusal rows for BEDC.Derived.HyperbolicFixedPointObstructionUp.}
\end{closurestatus}
