\chapter{A Concrete Naming Certificate for $\MetricReverseTriangleInequalityUp$}
\label{ch:concrete-instances-metric-reverse-triangle-inequality-namecert}
\origin{human}

Following Bishop and Bridges on constructive metric estimates, the $\MetricReverseTriangleInequalityUp$ packet records the finite route behind the estimate $|d(x,z)-d(y,z)| \leq d(x,y)$ without appealing to a host absolute-value operator or an ambient real-order theorem. It sits over the distance rows of \autoref{ch:concrete-instances-metric-namecert}, the order-and-operation surface of \autoref{ch:concrete-instances-real-alg-order-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, and the regular-Cauchy reverse-triangle route of \autoref{ch:concrete-instances-regular-cauchy-reverse-triangle-namecert}. The chapter packages the standard metric reverse-triangle estimate as finite BEDC NameCert data at L10 Phase Real and Completion.

\begin{definition}[Metric reverse-triangle inequality carrier]
\label{def:metric-reverse-triangle-inequality-carrier}
A $\MetricReverseTriangleInequalityUp$ carrier is a finite $\BHist$ packet
$$
T=(M,D_{xz},D_{yz},G,E,W,R,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricUp$ carrier row exposing only the finite distance surface and its local metric NameCert data.
\item $D_{xz}$ and $D_{yz}$ are the two metric-distance rows for the displayed endpoint pairs $(x,z)$ and $(y,z)$.
\item $G$ is the absolute-gap comparison row for the expression $|d(x,z)-d(y,z)|$; it is read only through the $\RealAlgOrderUp$ operation-and-order surface.
\item $E$ is the $\DyadicRatCoreUp$ tolerance row recording the requested comparison precision and the budget used to compare the two distance readbacks.
\item $W$ is the finite $\StreamNameUp$ window data serving the two distance streams and the gap stream at the requested scale.
\item $R$ is the $\RegSeqRatUp$ readback row for the accepted distance rows and the accepted absolute-gap row.
\item $S$ is the terminal $\RealUp$ seal, reachable only after the distance rows, comparison row, dyadic tolerance row, stream windows, and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the metric carrier, distance rows, absolute-gap comparison, tolerance row, window data, readback, seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from any reverse-triangle-facing request through $M,D_{xz},D_{yz},G,E,W,R,S,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MetricReverseTriangleInequalityUp$, $\MetricUp$, $\RealAlgOrderUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularCauchyReverseTriangleUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MetricReverseTriangleInequalityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,D_{xz},D_{yz},G,E,W,R,S,H,C,P,N$. The carrier has no coordinate for host absolute values, quotient real equality, open-cover compactness, selected nearest points, ambient $\RealUp$ completeness, Lean theorem checking, or bridge checking.
\end{definition}
\leandef{BEDC.Derived.MetricReverseTriangleInequalityUp}

\begin{theorem}[Metric reverse-triangle NameCert obligations]
\label{thm:metric-reverse-triangle-inequality-namecert-obligations}
For every accepted $\MetricReverseTriangleInequalityUp$ carrier
$$
T=(M,D_{xz},D_{yz},G,E,W,R,S,H,C,P,N),
$$
the local $\NameCert_{\MetricReverseTriangleInequalityUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the $\MetricUp$ row, the two metric-distance rows, the absolute-gap comparison row, the dyadic tolerance row, finite stream windows, regular readback, Real seal, and structural rows;
\item metric distance exposure, requiring $D_{xz}$ and $D_{yz}$ to be read only through the finite distance surface of $M$ before the absolute-gap comparison is available;
\item comparison and tolerance exactness, requiring $G$ and $E$ to record the absolute-gap comparison through $\RealAlgOrderUp$ and $\DyadicRatCoreUp$ at the displayed precision scale;
\item readback and seal nonescape, requiring $W,R,S$ to place the finite $\StreamNameUp$ windows and $\RegSeqRatUp$ readback before any $\RealUp$ consumer receives the estimate;
\item componentwise transport, continuation replay, package provenance, and local naming, requiring $H,C,P,N$ to preserve and name exactly the same finite reverse-triangle packet.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}

\begin{theorem}[Metric reverse-triangle distance-gap factorization]
\label{thm:metric-reverse-triangle-inequality-distance-gap}
For every accepted $\MetricReverseTriangleInequalityUp$ carrier $T=(M,D_{xz},D_{yz},G,E,W,R,S,H,C,P,N)$, every accepted read of the gap $|d(x,z)-d(y,z)|$ factors through the displayed metric rows $D_{xz},D_{yz}$ before it reaches the comparison row $G$. The comparison then passes through the $\RealAlgOrderUp$ operation-and-order surface, the $\DyadicRatCoreUp$ tolerance row $E$, the finite $\StreamNameUp$ windows $W$, and the $\RegSeqRatUp$ readback $R$ before the terminal $\RealUp$ seal $S$ is exposed.
\end{theorem}

\closureat{MetricReverseTriangleInequalityUp}{seedStr}

\begin{closurestatus}{\MetricReverseTriangleInequalityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metric-reverse-triangle-inequality-carrier}, \autoref{thm:metric-reverse-triangle-inequality-namecert-obligations}, and \autoref{thm:metric-reverse-triangle-inequality-distance-gap} seed the finite metric reverse-triangle route through displayed distance rows, absolute-gap comparison, dyadic tolerance, finite windows, regular readback, and Real seal data.}
  \formalstatus{\unformalizedV}
  \leantarget{BEDC.Derived.MetricReverseTriangleInequalityUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host absolute values, quotient real equality, open-cover compactness, selected nearest points, $\RealUp$ completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, metric distance exposure, comparison and tolerance exactness, readback and seal nonescape, componentwise transport, replay, provenance, and local naming for BEDC.Derived.MetricReverseTriangleInequalityUp.}
  \constructivestory{A $\MetricReverseTriangleInequalityUp$ packet is generated from a MetricUp carrier, two metric-distance rows, a RealAlgOrder absolute-gap comparison row, a DyadicRatCore tolerance row, finite StreamName windows, a RegSeqRat readback, a RealUp seal, componentwise transport, continuation replay, package provenance, and local naming.}
\end{closurestatus}
