\chapter{A Concrete Naming Certificate for $\FiniteOrthonormalBasisUp$}
\label{ch:concrete-instances-finite-orthonormal-basis-namecert}
\origin{human}

Following finite-dimensional linear algebra, Gram--Schmidt, and standard inner-product-space treatments, the $\FiniteOrthonormalBasisUp$ packet records the certificate surface that turns a displayed finite spanning list into a named finite orthonormal-basis row. It consumes the orthogonalization route of \autoref{ch:concrete-instances-gram-schmidt-namecert}, the vector carrier of \autoref{ch:concrete-instances-vecspace-namecert}, the inner-product form rows of \autoref{ch:concrete-instances-innerproduct-namecert}, the norm-one boundary of \autoref{ch:concrete-instances-norm-namecert}, and the finite coordinate ledger of \autoref{ch:concrete-instances-matrix-namecert}. The packet names only the finite selected-row certificate; it is not an infinite basis principle, a host vector equality theorem, a quotient representative selector, or an ambient completion object.

\begin{definition}[Finite orthonormal basis carrier]
\label{def:finite-orthonormal-basis-carrier}
A $\FiniteOrthonormalBasisUp$ carrier is a finite $\BHist$ packet
$$
B=(V,S,G,O,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $V$ is the $\VecSpaceUp$ source row, including the displayed zero, addition, scalar action, and finite carrier reads used by the packet.
\item $S$ is the finite spanning-list row whose entries are the only vectors eligible for the basis route.
\item $G$ is the $\GramSchmidtUp$ handoff row, exposing the finite orthogonalization replay applied to $S$.
\item $O$ is the orthogonality and norm-one row, displaying pairwise inner-product-zero checks and unit norm checks for the promoted rows.
\item $Q$ is the coordinate and reconstruction ledger, recording the finite coefficient rows through which a consumer reconstructs displayed vectors from the promoted rows.
\item $R$ is the refusal and boundary row, recording each discarded zero residual or non-promoted vector without selecting a replacement outside $S$.
\item $H$ records componentwise $\hsame$ transport for vector-space data, source rows, Gram--Schmidt replay, orthonormal rows, coordinate rows, refusal rows, continuation, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from the source list through Gram--Schmidt, norm-one promotion, coordinate reconstruction, and local certificate.
\item $P$ is the $\Pkg$ provenance over $\FiniteOrthonormalBasisUp$, $\GramSchmidtUp$, $\VecSpaceUp$, $\InnerProductUp$, $\NormUp$, $\MatrixUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteOrthonormalBasisUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $V,S,G,O,Q,R,H,C,P,N$. It has no coordinate for infinite basis choice, host vector equality, quotient representatives, a selected basis outside the displayed rows, or ambient completion.
\end{definition}
\leanchecked{BEDC.Derived.FiniteOrthonormalBasisUp.FiniteOrthonormalBasisTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite orthonormal basis NameCert obligations]
\label{thm:finite-orthonormal-basis-namecert-obligations}
For every accepted $\FiniteOrthonormalBasisUp$ carrier $B=(V,S,G,O,Q,R,H,C,P,N)$, the local $\NameCert_{\FiniteOrthonormalBasisUp}$ surface has exactly five finite rows:
\begin{enumerate}
\item carrier admission for the vector-space source, spanning list, Gram--Schmidt handoff, orthogonality and norm-one checks, coordinate reconstruction, refusal boundary, transport, continuation, provenance, and local naming;
\item Gram--Schmidt route exposure, requiring every promoted basis row to be read through $G$ from the displayed source list $S$;
\item orthogonality and norm-one exposure, requiring the $\InnerProductUp$ and $\NormUp$ checks in $O$ to be displayed before a promoted row is exported as orthonormal;
\item coordinate and reconstruction handoff, requiring every finite coordinate row and reconstruction read to pass through $Q$ and the finite $\MatrixUp$ ledger;
\item ledger non-escape from selected bases outside $S$, infinite basis choice, host vector equality, quotient representatives, and ambient completion.
\end{enumerate}
No accepted finite orthonormal-basis read has an obligation outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-orthonormal-basis-carrier}. The rows $V,S,G,O,Q,R,H,C,P,N$ are the only displayed rows available to a local $\NameCert_{\FiniteOrthonormalBasisUp}$ read.

The route first fixes the vector-space source row $V$ and the finite spanning list $S$. The Gram--Schmidt handoff row $G$ then exposes the finite orthogonalization replay, while the refusal row $R$ records every discarded zero residual or non-promoted vector.

The promoted rows are inspected through $O$. Orthogonality is read through displayed $\InnerProductUp$ checks, and unit length is read through displayed $\NormUp$ checks, so no host orthonormality predicate is imported.

Finally the coordinate ledger $Q$ supplies finite reconstruction through the $\MatrixUp$ rows, and $H,C,P,N$ transport, replay, source, and name the same finite route. Since no excluded coordinate appears in the carrier, the ledger cannot escape to infinite basis choice, host vector equality, quotient representatives, or ambient completion.
\end{proof}

\begin{theorem}[Finite orthonormal basis Gram--Schmidt handoff]
\label{thm:finite-orthonormal-basis-gram-schmidt-handoff}
Every $\FiniteOrthonormalBasisUp$ consumer that reads an orthonormal row, a coordinate row, or a reconstruction row from an accepted carrier $B=(V,S,G,O,Q,R,H,C,P,N)$ must first pass through the $\GramSchmidtUp$ handoff row $G$. The consumer therefore receives a finite route from the displayed spanning list to promoted orthonormal rows and coefficient reconstruction, not an infinite basis selector or an ambient completion principle.
\end{theorem}
\begin{proof}
Read the carrier rows of \autoref{def:finite-orthonormal-basis-carrier}. The only route from the finite source list $S$ to promoted rows is the Gram--Schmidt handoff $G$ followed by the orthogonality and norm-one row $O$.

The coordinate and reconstruction ledger $Q$ is downstream of that promoted-row surface. It can expose finite coefficients only after $G$ and $O$ have displayed the orthonormal rows they reference.

Apply the obligation surface of \autoref{thm:finite-orthonormal-basis-namecert-obligations}. Its non-escape row excludes selected bases outside $S$, infinite basis choice, host vector equality, quotient representatives, and ambient completion, so every exported consumer read remains on the displayed Gram--Schmidt route.
\end{proof}

\closureat{FiniteOrthonormalBasisUp}{seedStr}

\begin{closurestatus}{\FiniteOrthonormalBasisUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-orthonormal-basis-carrier}, \autoref{thm:finite-orthonormal-basis-namecert-obligations}, and \autoref{thm:finite-orthonormal-basis-gram-schmidt-handoff} seed the finite orthonormal-basis packet over displayed vector-space, Gram--Schmidt, inner-product, norm, matrix, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close infinite basis choice, host vector equality, quotient representatives, ambient completion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Gram--Schmidt route exposure, orthogonality and norm-one exposure, coordinate reconstruction handoff, and ledger non-escape for BEDC.Derived.FiniteOrthonormalBasisUp.}
  \constructivestory{A $\FiniteOrthonormalBasisUp$ packet is generated from a VecSpaceUp source row, a finite spanning-list row, a GramSchmidtUp handoff, displayed orthogonality and norm-one checks, a finite coordinate reconstruction ledger, refusal rows, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
