\chapter{A Concrete Naming Certificate for $\DirichletBoxApproximationUp$}
\label{ch:concrete-instances-dirichlet-box-approximation-namecert}
\origin{human}

Following Dirichlet's approximation theorem and Bishop--Bridges constructive analysis, the $\DirichletBoxApproximationUp$ packet names the finite pigeonhole route from a rational source row and a denominator box ledger to a rational approximation surface. It sits after the rational source of \autoref{ch:concrete-instances-rat-namecert}, the adjacent rational routes of \autoref{ch:concrete-instances-farey-sequence-namecert} and \autoref{ch:concrete-instances-stern-brocot-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet records only finite box partitions, displayed adjacent-rational handoffs, tolerance rows, readback windows, transport, replay, provenance, and local naming.

\begin{definition}[Dirichlet box approximation carrier]
\label{def:dirichlet-box-approximation-carrier}
A $\DirichletBoxApproximationUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,L,F,A,D,W,G,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\RatUp$ source row. It records the rational input data, finite numerator observations, and rational endpoints inspected by the approximation request.
\item $L$ is the denominator-box ledger. It stores the positive finite denominator bound, the box count, the inspected residue slots, and the finite comparison rows used to expose two entries in the same box.
\item $F$ is the finite box-partition row. It records the displayed partition of the unit interval or rational bracket into denominator-controlled cells.
\item $A$ is the adjacent-rational handoff row. It sends the same-pigeonhole pair to the $\FareySequenceUp$ or $\SternBrocotUp$ adjacency surface before any approximant is exported.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row. It stores the dyadic error request, slack ledger, and endpoint comparisons used to validate the rational difference produced by $L,F,A$.
\item $W$ is the $\StreamNameUp$ finite-window row. It schedules the finite observations of $Q,L,F,A,D$ that downstream real-facing requests may inspect.
\item $G$ is the $\RegSeqRatUp$ readback row. It repackages the displayed windows and rational differences as regular rational data before the terminal real seal is available.
\item $E$ is the $\RealUp$ seal row. It is reachable only after the rational source, box ledger, partition, adjacency handoff, dyadic tolerance, finite windows, and regular readback rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for rational sources, denominator boxes, partitions, adjacency handoffs, dyadic tolerances, finite windows, regular readback, Real seals, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a box-approximation request through $Q,L,F,A,D,W,G,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DirichletBoxApproximationUp$, $\RatUp$, $\FareySequenceUp$, $\SternBrocotUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DirichletBoxApproximationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,L,F,A,D,W,G,E,H,C,P,N$. It has no coordinate for selected best approximants, quotient real equality, trichotomy, countable choice, a host pigeonhole selector outside the finite ledger, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Dirichlet box approximation NameCert obligations]
\label{thm:dirichlet-box-approximation-namecert-obligations}
For every accepted $\DirichletBoxApproximationUp$ carrier
$$
B=(Q,L,F,A,D,W,G,E,H,C,P,N),
$$
the local $\NameCert_{\DirichletBoxApproximationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the rational source, denominator-box ledger, finite partition, adjacency handoff, dyadic tolerance, StreamName window, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming rows;
\item box partition exposure, requiring $L$ and $F$ to display the finite denominator-controlled cells and the same-box pair before an approximating rational difference can be exported;
\item adjacency transport, requiring $A$ to route the displayed same-box pair through the $\FareySequenceUp$ or $\SternBrocotUp$ sibling surface;
\item dyadic-error control, requiring $D$ to record the requested dyadic tolerance, slack, and endpoint comparisons used by the approximation read;
\item $\RegSeqRatUp$ and $\RealUp$ nonescape, requiring $W,G,E$ to stay downstream of the finite box and adjacency rows;
\item local naming, requiring $H,C,P,N$ to preserve and source exactly the displayed packet.
\end{enumerate}
No Dirichlet-box obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dirichlet-box-approximation-carrier}. The accepted packet displays exactly the rational source, denominator-box ledger, finite partition, adjacency handoff, dyadic tolerance, finite windows, regular readback, terminal Real seal, and structural rows listed in the statement.

The box partition exposure is finite. The row $L$ stores the denominator bound, box count, residue slots, and same-box comparison, while $F$ records the displayed partition cells. Together they supply the pigeonhole surface without invoking a host selector beyond the stored finite ledger.

Adjacency transport is read next. The row $A$ sends the same-box pair to the Farey and Stern--Brocot siblings of \autoref{ch:concrete-instances-farey-sequence-namecert} and \autoref{ch:concrete-instances-stern-brocot-namecert}, so the exported rational difference is attached to displayed adjacent-rational data.

The dyadic and real-facing rows remain downstream. The tolerance row $D$ supplies the error and slack comparisons, the window row $W$ schedules only finite observations, and $G$ reads those windows as $\RegSeqRatUp$ data before $E$ seals the route as a $\RealUp$-facing packet.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since the carrier contains no coordinate for selected best approximants, quotient real equality, trichotomy, countable choice, a host pigeonhole selector outside the finite ledger, or ambient completeness, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Dirichlet box approximation finite pigeonhole route]
\label{thm:dirichlet-box-approximation-finite-pigeonhole-route}
Every $\RegSeqRatUp$ or $\RealUp$ read exported by an accepted $\DirichletBoxApproximationUp$ carrier
$$
B=(Q,L,F,A,D,W,G,E,H,C,P,N)
$$
factors through the finite route
$$
Q,L,F,A,D,W \longmapsto G,E .
$$
Thus the exported approximation is witnessed by rational source data, a denominator-box ledger, a finite partition row, an adjacent-rational handoff, a dyadic tolerance row, and a finite StreamName window, not by quotient real equality, trichotomy, countable choice, selected best approximants, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with a regular-rational or Real-facing read from the accepted carrier. The only rows with that target are $G$ and $E$, and the carrier places them after $Q,L,F,A,D,W$.

The source and box rows determine the finite pigeonhole data. The row $Q$ supplies the rational observations, while $L$ and $F$ expose the denominator bound, partition cells, and same-box comparison needed for the approximating rational difference.

The adjacency and tolerance rows then control the exported approximation. The row $A$ records the Farey or Stern--Brocot handoff, and $D$ records the dyadic error and slack comparisons attached to that handoff.

Only after the finite window row $W$ is fixed can $G$ read the packet as regular rational data and $E$ seal it as Real-facing. Transport, replay, provenance, and local naming preserve this route through $H,C,P,N$, so none of the excluded ambient principles can enter the exported read.
\end{proof}

\falsifiablePrediction{Every $\DirichletBoxApproximationUp$ Real-facing read passes through $\RatUp$, $\FareySequenceUp$ or $\SternBrocotUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before any approximation output is visible.}

\independenceWitness{rat, farey-sequence, stern-brocot, dyadicratcore, streamname, regseqrat, real: $\DirichletBoxApproximationUp$ is not bijective to any listed sibling because it jointly carries a rational source row, denominator-box ledger, finite partition, adjacent-rational handoff, dyadic tolerance row, finite windows, regular readback, a Real seal, transport, replay, provenance, and local naming.}

\closureat{DirichletBoxApproximationUp}{seedStr}

\begin{closurestatus}{\DirichletBoxApproximationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dirichlet-box-approximation-carrier}, \autoref{thm:dirichlet-box-approximation-namecert-obligations}, and \autoref{thm:dirichlet-box-approximation-finite-pigeonhole-route} seed the finite pigeonhole route from rational source rows through denominator boxes, finite partitions, adjacency handoffs, dyadic tolerance, finite windows, regular readback, terminal Real sealing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected best approximants, quotient real equality, trichotomy, countable choice, host pigeonhole selectors outside the displayed finite ledger, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, box partition exposure, adjacency transport, dyadic-error control, StreamName and RegSeqRat readback ordering, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.DirichletBoxApproximationUp.}
  \constructivestory{A $\DirichletBoxApproximationUp$ packet is generated from RatUp source rows, a denominator-box ledger, a finite partition row, a FareySequenceUp or SternBrocotUp adjacency handoff, a DyadicRatCoreUp tolerance row, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
