\chapter{A Concrete Naming Certificate for $\RademacherUp$}
\label{ch:concrete-instances-rademacher-namecert}
\origin{human}

Following Rademacher's differentiability theorem for Lipschitz maps, the $\RademacherUp$ packet records only the finite dyadic-window derivative-candidate data that a BEDC consumer may inspect before any measure-theoretic almost-everywhere conclusion is visible. It sits over the Lipschitz carrier of \autoref{ch:concrete-instances-lipschitz-function-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the metric-space carrier of \autoref{ch:concrete-instances-metric-namecert}, and the absolute-continuity route of \autoref{ch:concrete-instances-absolute-continuous-function-namecert}. The packet names the finite frontier at which difference quotients, local Lipschitz bounds, dyadic radii, metric neighborhoods, and absolute-continuity control are displayed; it does not claim Lebesgue almost-everywhere differentiability, a measurable exceptional set, a selected derivative, an ambient measure algebra, or completion of a derivative space.

\begin{definition}[Rademacher carrier]
\label{def:rademacher-carrier}
A $\RademacherUp$ carrier is a finite $\BHist$ packet
$$
R=(L,E,D,M,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LipschitzFunctionUp$ row, exposing the source and target metric rows, graph ledger, Lipschitz bound, and distance-inequality route inspected by the packet.
\item $E$ is the $\RealUp$ seal row for the base point, output windows, and finite difference-quotient values read by downstream Real-facing consumers.
\item $D$ is the $\DyadicRatCoreUp$ endpoint-radius and tolerance ledger. It records the dyadic radii, halved-radius refinements, and comparison budgets used to build the displayed derivative-candidate windows.
\item $M$ is the $\MetricSpaceUp$ neighborhood row for the source and target distance requests used by the Lipschitz and difference-quotient checks.
\item $A$ is the $\AbsolutelyContinuousFunctionUp$ control row, recording only the finite interval or curve-window budget that bounds the visible variation consumed by the derivative-candidate packet.
\item $H$ records componentwise $\hsame$ transport for the Lipschitz row, Real seals, dyadic ledger, metric neighborhoods, absolute-continuity control, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a Rademacher-facing finite request through $D,M,L,A$, and finally into the terminal Real seal $E$.
\item $P$ is the $\Pkg$ provenance over $\RademacherUp$, $\LipschitzFunctionUp$, $\RealUp$, $\DyadicRatCoreUp$, $\MetricSpaceUp$, $\AbsolutelyContinuousFunctionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RademacherUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $L,E,D,M,A,H,C,P,N$. It has no coordinate for Lebesgue almost-everywhere differentiability, measurable null sets, host derivative functions, quotient maps, selected pointwise derivatives, countable-choice schedules, ambient measure completion, or completed function spaces.
\end{definition}

\begin{theorem}[Rademacher NameCert obligations]
\label{thm:rademacher-namecert-obligations}
For every accepted $\RademacherUp$ carrier
$$
R=(L,E,D,M,A,H,C,P,N),
$$
the local $\NameCert_{\RademacherUp}$ surface consists exactly of carrier admission, Lipschitz-row exposure, Real seal routing, dyadic endpoint-radius accounting, metric-neighborhood inspection, absolute-continuity control, componentwise transport, displayed replay, provenance, local naming, and non-escape from the displayed rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:rademacher-carrier}. The visible analytic rows are $L,E,D,M,A$, and the visible support rows are $H,C,P,N$.

The derivative-candidate route is finite. The Lipschitz row supplies the graph and bound data, the dyadic ledger supplies the inspected radii and tolerances, and the metric row supplies the neighborhoods in which those finite requests are read.

The Real and absolute-continuity rows do not add a measure theorem. The Real row seals only the displayed numerical windows, while the absolute-continuity row records the finite variation-control budget used by those windows.

Finally $H$ and $C$ transport and replay the same coordinates, and $P,N$ source and name the packet. Since no other coordinate occurs in the carrier, the NameCert surface exports none of the excluded measurable, derivative-selection, quotient, choice, completion, or ambient almost-everywhere data.
\end{proof}

\begin{theorem}[Rademacher finite derivative-candidate packet]
\label{thm:rademacher-finite-derivative-candidate-packet}
Every Real-facing read exported by an accepted $\RademacherUp$ carrier factors through the finite route
$$
D,M,L,A \longmapsto E
$$
before any derivative-candidate value is consumed. The displayed packet records dyadic radii, metric neighborhoods, Lipschitz distance bounds, absolute-continuity variation control, and terminal Real seals, but it does not assert that the derivative candidate exists on a Lebesgue almost-everywhere set or that the candidate is selected outside the displayed finite windows.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $R=(L,E,D,M,A,H,C,P,N)$. By \autoref{thm:rademacher-namecert-obligations}, the only Real-facing row is $E$, and it is downstream of the dyadic, metric, Lipschitz, and absolute-continuity rows.

The dyadic and metric rows are indispensable because the finite difference-quotient request needs displayed endpoint radii and the source and target neighborhoods in which the Lipschitz comparison is read. The Lipschitz row is indispensable because it supplies the graph and bound ledger for the same finite request.

The absolute-continuity row records the finite variation-control budget attached to the inspected windows. It is not a measure-completion row and does not select derivatives outside those windows.

Transport, replay, provenance, and local naming preserve the same route. Thus every Real-facing derivative-candidate read reaches the seal only through $D,M,L,A$, with no Lebesgue almost-everywhere theorem, exceptional-set algebra, selected derivative, quotient stream, countable-choice schedule, or ambient completeness coordinate added.
\end{proof}

\closureat{RademacherUp}{seedStr}

\begin{closurestatus}{\RademacherUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:rademacher-carrier}, \autoref{thm:rademacher-namecert-obligations}, and \autoref{thm:rademacher-finite-derivative-candidate-packet} seed the finite derivative-candidate route over Lipschitz, Real, DyadicRatCore, MetricSpace, absolute-continuity, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lebesgue almost-everywhere differentiability, measurable exceptional sets, selected derivatives, quotient maps, countable choice, ambient measure completion, completed derivative spaces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Lipschitz-row exposure, Real seal routing, dyadic endpoint-radius accounting, metric-neighborhood inspection, absolute-continuity control, transport stability, replay stability, provenance, local naming, and non-escape for BEDC.Derived.RademacherUp.}
  \constructivestory{A $\RademacherUp$ packet is generated from a LipschitzFunction row, RealUp seal row, DyadicRatCore endpoint-radius ledger, MetricSpace neighborhood row, AbsolutelyContinuousFunction control row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
