\chapter{A Concrete Naming Certificate for $\FiniteWindowCompactnessUp$}
\label{ch:concrete-instances-finite-window-compactness-namecert}
\origin{human}

Following Bishop and Bridges on compact metric intervals and constructive finite covers, the $\FiniteWindowCompactnessUp$ packet records compactness as explicit dyadic finite-net windows whose radius ledger can be consumed by compact-uniform-continuity. It realizes the finite-window route of \autoref{ch:visions-compact-uniform-continuity} over the compact source of \autoref{ch:concrete-instances-compactmetric-namecert}, the metric rows of \autoref{ch:concrete-instances-metric-namecert}, the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the closed bounded interval route of \autoref{ch:concrete-instances-closed-bounded-interval-uniform-modulus-namecert}, the finite lower-bound fold of \autoref{ch:concrete-instances-finite-lower-bound-fold-namecert}, and the downstream uniform-modulus handoff of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet names finite windows and ledger rows only; it does not import open-cover compactness, selected subcovers outside the displayed bundle, quotient point equality, ambient real completeness, Lean verification, or bridge checking.

\begin{definition}[FiniteWindowCompactness carrier]
\label{def:finite-window-compactness-carrier}
A $\FiniteWindowCompactnessUp$ carrier is a finite $\BHist$ packet
$$
W=(K,M,D,I,G,L,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row exposing the compact metric witness through finite inspection data.
\item $M$ is the $\MetricUp$ distance row used to compare each displayed center with a requested point.
\item $D$ is the $\DyadicRatCoreUp$ radius ledger containing the positive mesh scale and its tolerance comparisons.
\item $I$ is the closed bounded interval or bounded compact source row when the packet is used over a real interval.
\item $G$ is the finite window grid, a displayed $\mathsf{ProbeBundle}$ of dyadic centers with coverage witnesses.
\item $L$ is the finite lower-bound fold row consumed after the window grid has exposed its positive candidate radii.
\item $U$ is the $\UniformModulusUp$ handoff row that receives the tolerance-only modulus budget.
\item $H$ records componentwise $\hsame$ transport for $K,M,D,I,G,L,U$ and the structural rows.
\item $C$ records displayed $\Cont$ replay from compact finite windows to the lower-bound fold and uniform-modulus handoff.
\item $P$ is the $\Pkg$ provenance over $\FiniteWindowCompactnessUp$, $\CompactMetricUp$, $\MetricUp$, $\DyadicRatCoreUp$, $\FiniteLowerBoundFoldUp$, $\UniformModulusUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FiniteWindowCompactnessUp}$ row.
\end{enumerate}
The carrier contains no arbitrary open-cover object, no selected subcover outside $G$, no quotient point equality, no host finite minimum, and no ambient $\RealUp$ completeness row.
\end{definition}

\begin{theorem}[FiniteWindowCompactness NameCert obligations]
\label{thm:finite-window-compactness-namecert-obligations}
For every accepted $\FiniteWindowCompactnessUp$ carrier
$$
W=(K,M,D,I,G,L,U,H,C,P,N),
$$
the local $\NameCert_{\FiniteWindowCompactnessUp}$ surface consists exactly of compact metric source exposure, metric distance readback, dyadic positive-radius admission, interval-source localization when present, finite window-grid coverage, lower-bound fold handoff, uniform-modulus delivery, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-compactness-carrier}. The accepted packet exposes only the compact metric source, metric-distance row, dyadic radius ledger, optional interval source, finite grid, fold row, uniform-modulus row, and structural rows.

The grid row $G$ is the finite inspection domain. Each center and coverage witness is read together with $D$, so the compactness consumer receives a dyadic window bundle rather than an arbitrary open cover.

The lower-bound row $L$ is then read after the window candidates are visible. Its output is the only route into the uniform-modulus handoff $U$, while $H,C,P,N$ preserve and name the same displayed route.
\end{proof}

\begin{theorem}[FiniteWindowCompactness uniform-modulus route]
\label{thm:finite-window-compactness-uniform-modulus-route}
Every compact-uniform-continuity consumer that reads a $\FiniteWindowCompactnessUp$ packet reaches $\UniformModulusUp$ only through
$$
K \to M \to D \to I \to G \to L \to U \to H \to C \to P \to N.
$$
Thus the consumer must first inspect the compact metric source, the metric distance row, the dyadic finite-window ledger, the interval source when present, and the finite lower-bound fold before it receives a tolerance-only uniform-modulus row.
\end{theorem}
\begin{proof}
Start with an accepted carrier $W=(K,M,D,I,G,L,U,H,C,P,N)$. A compactness read begins at $K$, and any distance comparison needed by the window coverage row must pass through $M$.

The dyadic ledger $D$ supplies positive mesh and tolerance comparisons. If the source is a closed bounded interval, the interval row $I$ is read as the displayed boundary for the finite dyadic window.

The finite grid $G$ then supplies the only centers and coverage witnesses available to the consumer. The lower-bound fold $L$ reads those finite candidates and delivers the resulting precision to $U$.

The rows $H,C,P,N$ transport, replay, source, and name the same route. Since no excluded host cover, selected subcover, quotient equality, host minimum, or ambient completeness coordinate occurs in the carrier, the displayed chain exhausts the uniform-modulus access path.
\end{proof}

\closureat{FiniteWindowCompactnessUp}{seedStr}

\begin{closurestatus}{\FiniteWindowCompactnessUp}
  \constructivestory{A $\FiniteWindowCompactnessUp$ packet is generated from a CompactMetricUp source row, a MetricUp distance row, a DyadicRatCoreUp radius ledger, an optional closed bounded interval row, finite ProbeBundle window grids, a FiniteLowerBoundFoldUp row, a UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-window-compactness-carrier}, \autoref{thm:finite-window-compactness-namecert-obligations}, and \autoref{thm:finite-window-compactness-uniform-modulus-route} seed the finite dyadic window route from compact metric data to uniform-modulus consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected subcovers outside the displayed window, quotient point equality, host finite minima, ambient real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked compact source exposure, dyadic radius admission, finite grid coverage, lower-bound fold delivery, uniform-modulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.FiniteWindowCompactnessUp.}
\end{closurestatus}
