\chapter{A Concrete Naming Certificate for $\BishopCauchyDisplayCertificateUp$}
\label{ch:concrete-instances-bishop-cauchy-display-certificate-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\BishopCauchyDisplayCertificateUp$ packet records a displayed Cauchy certificate as finite BEDC NameCert data before any Real seal or completion-facing read is consumed. It sits between the criterion surface of \autoref{ch:concrete-instances-bishop-cauchy-criterion-namecert}, the criterion-to-completion route of \autoref{ch:concrete-instances-bishop-cauchy-criterion-completion-namecert}, the reusable tail certificate of \autoref{ch:concrete-instances-regular-cauchy-tail-certificate-namecert}, the modulus schedule surface of \autoref{ch:concrete-instances-cauchy-modulus-space-namecert}, the stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives L10 Real and Completion consumers a single finite display entry point; it is not a quotient stream equality theorem, a selected limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop Cauchy display-certificate carrier]
\label{def:bishop-cauchy-display-certificate-carrier}
A $\BishopCauchyDisplayCertificateUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,M,W,T,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\BishopCauchyCriterionUp$ row naming the finite Cauchy criterion whose display is being certified.
\item $M$ is the $\CauchyModulusSpaceUp$ row recording the displayed modulus schedules and precision requests used by $Q$.
\item $W$ is the $\StreamNameUp$ window row through which the source sequence, modulus requests, and tail comparisons are inspected.
\item $T$ is the $\RegularCauchyTailCertificateUp$ row witnessing that the displayed windows supply the shared tail certificate required by Real and Completion consumers.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from $W,T$, and the modulus schedule in $M$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic radii, comparison budgets, and slack rows used by the displayed criterion and tail handoff.
\item $E$ is the terminal $\RealUp$ seal row reached only after $Q,M,W,T,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $Q,M,W,T,R,D,E$ and the local naming row.
\item $C$ records displayed $\Cont$ replay from a display request through the criterion, modulus schedule, stream windows, tail certificate, rational readback, dyadic tolerance ledger, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\BishopCauchyDisplayCertificateUp$, $\BishopCauchyCriterionUp$, $\BishopCauchyCriterionCompletionUp$, $\CauchyModulusSpaceUp$, $\StreamNameUp$, $\RegularCauchyTailCertificateUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCauchyDisplayCertificateUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,M,W,T,R,D,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected representatives, selected limits, countable choice, trichotomy, host real equality, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Bishop Cauchy display-certificate NameCert obligations]
\label{thm:bishop-cauchy-display-certificate-namecert-obligations}
For every accepted $\BishopCauchyDisplayCertificateUp$ carrier
$$
B=(Q,M,W,T,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\BishopCauchyDisplayCertificateUp}$ surface consists exactly of carrier admission for the Bishop Cauchy criterion row, explicit Cauchy modulus schedules, finite $\StreamNameUp$ windows, $\RegularCauchyTailCertificateUp$ tail handoff, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance exposure, terminal $\RealUp$ seal exposure, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every Real or Completion consumer must expose $Q,M,W,T,R,D,E$ before $H,C,P,N$ can be consumed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-cauchy-display-certificate-carrier}. The analytic display rows are exactly $Q,M,W,T,R,D,E$, and the structural support rows are exactly $H,C,P,N$.

The criterion row $Q$ supplies the Bishop Cauchy request, while $M$ makes the precision schedule explicit. The stream row $W$ is therefore the only observation surface through which the sequence and modulus requests can be read.

The tail certificate $T$ then binds the displayed windows to the shared regular Cauchy tail route. The readback row $R$ and dyadic ledger $D$ keep the rational and tolerance data visible before the terminal Real seal $E$ is available.

Finally $H,C,P,N$ transport, replay, source, and name the same rows. Since no excluded host object is present as a carrier coordinate, these rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Bishop Cauchy display-certificate tail handoff]
\label{thm:bishop-cauchy-display-certificate-tail-handoff}
Every Real or Completion consumer accepted by a $\BishopCauchyDisplayCertificateUp$ carrier reads the shared tail certificate through the finite route
$$
\BishopCauchyCriterionUp \longmapsto \CauchyModulusSpaceUp \longmapsto \StreamNameUp \longmapsto \RegularCauchyTailCertificateUp \longmapsto \RegSeqRatUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp
$$
together with $H,C,P,N$. Consequently the consumer receives the displayed criterion, modulus schedule, finite windows, tail certificate, regular rational readback, dyadic tolerance ledger, and terminal Real seal, but it receives no selected limit, quotient stream equality, countable-choice schedule, trichotomy row, or ambient $\RealUp$ completeness witness.
\end{theorem}
\begin{proof}
Start with a Real or Completion read of $B$. The source criterion and precision schedule appear only as $Q$ and $M$, so the read must expose them before any window or tail row is available.

The row $W$ supplies the finite inspection surface. The handoff row $T$ is downstream of those windows and is the only coordinate that can expose a regular Cauchy tail certificate.

The rows $R,D,E$ then perform the regular rational readback, dyadic tolerance accounting, and terminal Real sealing in order. The support rows $H,C,P,N$ preserve that same route without adding analytic content.

Because quotient streams, selected limits, countable choice, trichotomy, and ambient completeness are absent from the carrier, no consumer can obtain them from the displayed tail handoff.
\end{proof}

\closureat{BishopCauchyDisplayCertificateUp}{seedStr}

\begin{closurestatus}{\BishopCauchyDisplayCertificateUp}
  \constructivestory{A $\BishopCauchyDisplayCertificateUp$ packet is generated from a BishopCauchyCriterion row, CauchyModulusSpace schedules, StreamName windows, a RegularCauchyTailCertificate handoff, RegSeqRat readback, DyadicRatCore tolerances, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-cauchy-display-certificate-carrier}, \autoref{thm:bishop-cauchy-display-certificate-namecert-obligations}, and \autoref{thm:bishop-cauchy-display-certificate-tail-handoff} seed the finite display-certificate route for the L10 Real and Completion surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected Cauchy representatives, selected limits, countable choice, trichotomy, host real equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, criterion exposure, modulus schedule exposure, finite-window exposure, tail-certificate handoff, RegSeqRat readback exactness, DyadicRatCore tolerance exposure, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopCauchyDisplayCertificateUp.}
\end{closurestatus}
