\chapter{A Concrete Naming Certificate for $\SequentiallyCompactCompletionUp$}
\label{ch:concrete-instances-sequentially-compact-completion-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\SequentiallyCompactCompletionUp$ packet records the finite route by which a totally bounded separated metric completion exposes sequential compactness through displayed subsequence windows. It sits between the total-bounded completion route of \autoref{ch:concrete-instances-totallyboundedcompletion-namecert}, the separated completion comparison of \autoref{ch:concrete-instances-separatedcompletion-namecert}, the compact metric completion seal of \autoref{ch:concrete-instances-compact-metric-completion-namecert}, the finite sequence-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a completion-facing subsequence certificate; it is not open-cover compactness, a quotient completion, a selected limit-point operation, countable choice, host sequence equality, or ambient $\RealUp$ completeness.

\begin{definition}[Sequentially compact completion carrier]
\label{def:sequentially-compact-completion-carrier}
A $\SequentiallyCompactCompletionUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,S,K,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the $\TotallyBoundedCompletionUp$ row. It records the source metric carrier, finite-net completion route, net refinement ledger, Cauchy-filter basis, dense embedding, and uniformly continuous handoff consumed by the sequential compactness request.
\item $S$ is the $\SeparatedCompletionUp$ row. It compares completed reads only through the displayed zero-distance and separated-equality route.
\item $K$ is the $\CompactMetricCompletionUp$ row. It supplies the complete totally bounded metric completion surface from which compact-facing consumers may request finite sequence data.
\item $W$ is the subsequence-window ledger. It stores the inspected $\StreamNameUp$ windows, the monotone selected-index rows, the finite tail requests, and the bounded-window evidence used by the compact metric completion surface.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the selected windows, rational tail budgets, and completion-facing Cauchy data.
\item $E$ is the terminal $\RealUp$ seal row reached only after $T,S,K,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the total-bounded completion route, separated completion comparison, compact metric completion surface, subsequence windows, regular rational readback, Real seal, continuation replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite sequence request through $T,S,K,W,R,E$.
\item $P$ is the $\Pkg$ provenance over $\SequentiallyCompactCompletionUp$, $\TotallyBoundedCompletionUp$, $\SeparatedCompletionUp$, $\CompactMetricCompletionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SequentiallyCompactCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,S,K,W,R,E,H,C,P,N$. It has no coordinate for open-cover compactness, quotient representatives, selected limit points outside $W$, countable-choice schedules, host sequence equality, host real equality, or detached ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[SequentiallyCompactCompletion NameCert obligations]
\label{thm:sequentially-compact-completion-namecert-obligations}
For every accepted $\SequentiallyCompactCompletionUp$ carrier
$$
Q=(T,S,K,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\SequentiallyCompactCompletionUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item carrier admission for the total-bounded completion route, separated completion comparison, compact metric completion surface, subsequence-window ledger, regular rational readback, Real seal, componentwise transport, displayed replay, provenance, and local naming row;
\item completion-route exposure, requiring every sequential compactness request to read $T$ and $S$ before it may inspect the compact metric completion row $K$;
\item subsequence-window locality, requiring selected indices, finite tails, source windows, and compactness evidence to be precisely the displayed rows in $W$;
\item $\RegSeqRatUp$ handoff exactness, requiring every convergence read to enter $R$ only from the windows and tail budgets stored in $W$ and transported through $H$;
\item $\RealUp$ seal nonescape, requiring the terminal limit read to pass through $E$ after $R$ and forbidding quotient streams, host real equality, external selected limits, countable choice, and detached ambient completeness;
\item provenance and naming closure, requiring $P$ and $N$ to name only the displayed packet and no principle absent from its rows.
\end{enumerate}
No NameCert obligation is stored outside these displayed rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:sequentially-compact-completion-carrier}. The projected rows are exactly the total-bounded completion route $T$, separated comparison $S$, compact metric completion surface $K$, subsequence-window ledger $W$, regular rational readback $R$, Real seal $E$, and structural rows $H,C,P,N$.

Completion-route exposure follows the sibling order. The finite total-bounded completion route of \autoref{ch:concrete-instances-totallyboundedcompletion-namecert} is read first through $T$, and the separated completion comparison of \autoref{ch:concrete-instances-separatedcompletion-namecert} is read through $S$ before the compact metric completion surface $K$ can be inspected.

Subsequence-window locality is internal to $W$. The packet stores the $\StreamNameUp$ windows, selected-index rows, finite tail requests, and bounded-window evidence that the compact metric completion surface uses; there is no separate coordinate from which an external subsequence or selected limit point could be read.

The convergence handoff is then the row $R$. It accepts only the selected windows and rational tail budgets displayed by $W$, with componentwise transport supplied by $H$, so the handoff cannot be replaced by quotient stream equality or host sequence equality.

Finally, the terminal read is sealed by $E$, while $C,P,N$ replay, source, and name the same route. Since the carrier has no coordinate for open-cover compactness, quotient completion, countable choice, host real equality, external selected limits, or detached ambient completeness of $\RealUp$, none of those data can be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[SequentiallyCompactCompletion subsequence seal]
\label{thm:sequentially-compact-completion-subsequence-seal}
Let $Q=(T,S,K,W,R,E,H,C,P,N)$ be an accepted $\SequentiallyCompactCompletionUp$ carrier. Every sequential-compactness-facing consumer factors through the finite route
$$
T,S \longmapsto K \longmapsto W \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
Consequently the consumer receives total-bounded completion data, separated completion comparison, compact metric completion, displayed subsequence windows, regular rational readback, Real seal, transport, replay, provenance, and local naming before it can read a completed subsequence limit.
\end{theorem}
\begin{proof}
Project the consumer read from the carrier. By \autoref{def:sequentially-compact-completion-carrier}, the only completion-facing rows available before the compact metric surface are $T$ and $S$.

The compact metric completion row $K$ is downstream of those completion rows. It exposes finite completion compactness only as the route already named in \autoref{ch:concrete-instances-compact-metric-completion-namecert}, so the consumer cannot bypass $T$ and $S$ by invoking an open-cover compactness theorem or a quotient completion.

The subsequence information is then exactly the ledger $W$. The regular rational readback $R$ and terminal Real seal $E$ are reachable only from the windows, selected indices, and tail budgets stored in that ledger.

Transport and replay through $H$ and $C$ preserve the same order, and $P,N$ name only that packet. This proves the displayed factorization and excludes external selected limits, countable choice, host sequence equality, host real equality, and detached ambient Real completeness.
\end{proof}

\falsifiablePrediction{Every $\SequentiallyCompactCompletionUp$ completed-subsequence read factors through TotallyBoundedCompletion, SeparatedCompletion, CompactMetricCompletion, StreamName subsequence windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{totallyboundedcompletion, separatedcompletion, compactmetriccompletion, streamname, regseqrat, real: $\SequentiallyCompactCompletionUp$ is not bijective to any listed sibling because it jointly carries completion route exposure, separated comparison, compact metric completion, displayed subsequence windows, rational readback, Real seal, transport, replay, provenance, and local naming.}

\closureat{SequentiallyCompactCompletionUp}{seedStr}

\begin{closurestatus}{\SequentiallyCompactCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sequentially-compact-completion-carrier}, \autoref{thm:sequentially-compact-completion-namecert-obligations}, and \autoref{thm:sequentially-compact-completion-subsequence-seal} seed the finite route from total-bounded separated completion data to displayed subsequence compactness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, quotient completion, selected limit points outside the displayed windows, countable choice, host sequence equality, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, completion-route exposure, subsequence-window locality, RegSeqRat handoff exactness, RealUp seal nonescape, provenance and naming closure, and TasteGate field faithfulness for BEDC.Derived.SequentiallyCompactCompletionUp.}
  \constructivestory{A $\SequentiallyCompactCompletionUp$ packet is generated from a TotallyBoundedCompletion route, a SeparatedCompletion comparison, a CompactMetricCompletion surface, StreamName subsequence windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
