\chapter{A Concrete Naming Certificate for $\PriestleyDualityUp$}
\label{ch:concrete-instances-priestley-duality-namecert}
\origin{human}

Following Priestley and Davey--Priestley, the $\PriestleyDualityUp$ packet records the finite BEDC naming surface for the ordered topological representation of bounded distributive lattices. It sits between the lattice rows of \autoref{ch:concrete-instances-lattice-namecert}, the complemented endpoint discipline of \autoref{ch:concrete-instances-booleanalgebra-namecert}, the indexed-open topology rows of \autoref{ch:concrete-instances-topology-namecert}, and the clopen-ledger bridge of \autoref{ch:concrete-instances-stoneduality-namecert}. The packet names order-separating clopen upsets and their finite continuity ledger; it does not import ultrafilters, selected prime filters, powerset topology, quotient lattice equality, or a host duality theorem.

\begin{definition}[Priestley duality carrier]
\label{def:priestley-duality-carrier}
A $\PriestleyDualityUp$ carrier is a finite $\BHist$ packet
$$
P=(L,B,T,S,U,O,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the bounded distributive-lattice source read through the $\LatticeUp$ carrier and its finite meet--join order rows.
\item $B$ is the Boolean endpoint comparison row available from the $\BooleanAlgebraUp$ neighbour when complemented clopen data is requested.
\item $T$ is the indexed-open $\TopologyUp$ row that records the finite open-neighbourhood observations used by the dual side.
\item $S$ is the Stone-facing clopen ledger from \autoref{ch:concrete-instances-stoneduality-namecert}, restricted to observations that are also upward-closed for the order read from $L$.
\item $U$ is the finite order-separation row: whenever two displayed lattice observations are separated by the order classifier, $U$ names a clopen upset containing the larger observation and excluding the smaller one.
\item $O$ is the order/topology compatibility row, recording that finite intersections, unions, complements used through $B$, and indexed opens used through $T$ preserve the clopen-upset route named by $S$ and $U$.
\item $H$ records componentwise $\hsame$ transport for $L,B,T,S,U,O,C,G,N$.
\item $C$ records displayed $\Cont$ replay from a lattice observation through the clopen-upset and topology rows.
\item $G$ is the $\Pkg$ provenance over $\LatticeUp$, $\BooleanAlgebraUp$, $\TopologyUp$, $\StoneDualityUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PriestleyDualityUp}$ row.
\end{enumerate}
The carrier contains no coordinate for ultrafilter selection, a host spectral space, unrestricted prime filters, quotient lattice equality, powerset topology, or classical choice.
\end{definition}

\begin{theorem}[Priestley duality NameCert obligations]
\label{thm:priestley-duality-namecert-obligations}
For every accepted $\PriestleyDualityUp$ carrier $P=(L,B,T,S,U,O,H,C,G,N)$, the local $\NameCert_{\PriestleyDualityUp}$ surface consists exactly of lattice-source admission through $L$, Boolean endpoint comparison through $B$, topology admission through $T$, Stone-facing clopen admission through $S$, finite order separation through $U$, order/topology compatibility through $O$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $G$, and local naming through $N$. Any downstream order/topology consumer must consume these rows before it can treat a clopen upset as a Priestley-duality observation.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:priestley-duality-carrier}. The rows $L,B,T,S,U,O$ are the only analytic and order-topology coordinates, and the rows $H,C,G,N$ only transport, replay, source, and name them.

The lattice-source obligation is read from $L$, while Boolean endpoint comparison and topology admission are read from $B$ and $T$. The Stone-facing clopen ledger $S$ supplies the clopen side, and $U$ restricts it to the finite upsets needed for order separation.

Compatibility is then checked by $O$. This row keeps the finite clopen-upset observations stable under the lattice and topology operations that are public through the cited neighbouring chapters.

Finally $H,C,G,N$ preserve and name the same route. Because the carrier has no ultrafilter, selected prime-filter, host spectral-space, powerset-topology, quotient-equality, or choice coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\closureat{PriestleyDualityUp}{seedStr}

\begin{closurestatus}{\PriestleyDualityUp}
  \constructivestory{A $\PriestleyDualityUp$ packet is generated from bounded distributive-lattice rows, Boolean endpoint comparisons, indexed topology observations, a Stone-facing clopen ledger, finite clopen-upset separation rows, order/topology compatibility, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:priestley-duality-carrier} and \autoref{thm:priestley-duality-namecert-obligations} seed the order/topology representation surface over lattice, Boolean-algebra, topology, and Stone-duality rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim an ultrafilter construction, selected prime filters, host spectral spaces, powerset topology, quotient lattice equality, Lean theorem verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite order-separation stability, clopen-upset topology compatibility, and local NameCert exhaustion for BEDC.Derived.PriestleyDualityUp.}
\end{closurestatus}
