\chapter{A Concrete Naming Certificate for $\CauchyFilterModulusUp$}
\label{ch:concrete-instances-cauchy-filter-modulus-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy completion, the $\CauchyFilterModulusUp$ packet names the finite modulus interface by which Cauchy-filter evidence becomes a regular rational handoff before a Real seal is read. It refines the filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the basis generator of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert}, and the regular rational route of \autoref{ch:concrete-instances-regseqrat-namecert}. Its consumer path also reads finite windows through \autoref{ch:concrete-instances-streamname-namecert}, dyadic ledgers through \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal boundary of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite modulus surface for Cauchy-filter completion data; it is not a quotient filter, selected limit, countable-choice schedule, host equality comparison, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.

\begin{definition}[Cauchy filter modulus carrier]
\label{def:cauchy-filter-modulus-carrier}
A $\CauchyFilterModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(F,B,G,S,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyFilterUp$ source row whose displayed precision requests must be regularized.
\item $B$ is the $\CauchyFilterBasisUp$ generator row. It names the finite basis elements and common-refinement witnesses used to inspect the requests in $F$.
\item $G$ is the $\RegularCauchyFilterUp$ regularity row. It records the finite tail-basis test that turns the source request and basis witness into a regular Cauchy-filter read.
\item $S$ is the $\StreamNameUp$ window row reached only after $F,B,G$ have been displayed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It stores the requested dyadic scale, the smaller scale certified by $G$, and the comparison used by the regular readback.
\item $R$ is the $\RegSeqRatUp$ handoff row. It repacks the accepted windows and dyadic ledger as a regular rational sequence row.
\item $E$ is the downstream $\RealUp$ seal boundary visible only after $F,B,G,S,D,R$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the filter source, basis generator, regularity row, windows, dyadic ledger, regular readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a filter precision request through $F,B,G,S,D,R,E$ in that order.
\item $P$ is the $\Pkg$ provenance over $\CauchyFilterModulusUp$, $\CauchyFilterUp$, $\CauchyFilterBasisUp$, $\RegularCauchyFilterUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyFilterModulusUp}$ row.
\end{enumerate}
The classifier compares accepted modulus packets only through the displayed route
$$
F,B,G \longmapsto S,D,R,E \longmapsto H,C,P,N .
$$
No carrier coordinate stores a quotient filter, selected limit, countable-choice schedule, host equality of filter values, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.
\end{definition}

\begin{theorem}[Cauchy filter modulus NameCert obligations]
\label{thm:cauchy-filter-modulus-namecert-obligations}
For every accepted $\CauchyFilterModulusUp$ carrier
$$
M=(F,B,G,S,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyFilterModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the Cauchy-filter source, basis generator, regularity row, window row, dyadic tolerance ledger, regular rational handoff, Real seal boundary, transport, replay, provenance, and local naming row;
\item source-to-basis routing, requiring each displayed filter precision request in $F$ to read its finite basis witness from $B$ before the regularity row is inspected;
\item regular filter modulus extraction, requiring $G$ to name the finite tail-basis test and the scale comparison that make the requested filter read regular;
\item window and dyadic replay, requiring $S,D$ to expose only the finite observations and dyadic budget attached to the same $F,B,G$ route;
\item regular readback and Real handoff, requiring $R$ to be read before the terminal $\RealUp$ boundary $E$ is visible to completion-facing consumers;
\item transport and replay stability, requiring $H$ and $C$ to preserve the order $F,B,G,S,D,R,E$ under componentwise $\hsame$ transport and displayed $\Cont$ replay;
\item provenance exhaustion, requiring $P,N$ to name only this finite modulus interface and to export no quotient filter, selected limit, countable-choice schedule, host equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-filter-modulus-carrier}. The projection exposes exactly the source filter, finite basis row, regularity row, stream windows, dyadic ledger, regular rational readback, terminal seal, and structural rows $H,C,P,N$.

The source-to-basis route is fixed by row order. A precision request first reads $F$ and then the finite basis witness supplied by $B$; the packet has no coordinate that can jump directly from a filter request to a regular sequence.

The regularity row $G$ performs the modulus extraction. It names the finite tail-basis test and the scale comparison used to justify the regular Cauchy read, so the modulus is packet data rather than an ambient completeness or choice principle.

The replay row $C$ then carries the same request through $S,D,R,E$. Transport in $H$ preserves these displayed rows, while $P,N$ source and name only the packet; therefore the excluded quotient, selected-limit, choice, host-equality, completeness, Lean-verification, and bridge-checking data are outside the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy filter modulus regular readback]
\label{thm:cauchy-filter-modulus-regular-readback}
Let
$$
M=(F,B,G,S,D,R,E,H,C,P,N)
$$
be an accepted $\CauchyFilterModulusUp$ carrier. Every displayed Cauchy-filter precision request factors through a finite regular readback route
$$
F \longmapsto B \longmapsto G \longmapsto S,D \longmapsto R .
$$
Consequently the packet exports a $\RegSeqRatUp$ row only after the source filter request has been witnessed by a basis row, checked by the regular Cauchy-filter row, and replayed through the finite window and dyadic tolerance rows.
\end{theorem}
\begin{proof}
Start with a displayed precision request in $F$. The carrier exposes no direct $\RegSeqRatUp$ coordinate from $F$, so the request must first be read through the finite basis row $B$.

Next inspect $G$. This row attaches the basis witness to the regular Cauchy-filter test and records the smaller scale used by the modulus request.

The finite observations then pass through $S$ and the dyadic comparison through $D$. These rows are tied to the same source and basis data by carrier projection and componentwise transport.

Finally $R$ repacks the accepted finite observations and tolerance ledger as a regular rational sequence row. Thus the regular readback is exported only through the displayed route.
\end{proof}

\begin{theorem}[Cauchy filter modulus Real handoff]
\label{thm:cauchy-filter-modulus-real-handoff}
Every completion-facing or $\RealUp$-facing consumer of an accepted $\CauchyFilterModulusUp$ carrier
$$
M=(F,B,G,S,D,R,E,H,C,P,N)
$$
reaches the terminal seal $E$ only through the finite route
$$
F,B,G,S,D,R \longmapsto E \longmapsto H,C,P,N .
$$
In particular, the consumer receives a Cauchy-filter source row, Cauchy-filter basis row, regular Cauchy-filter row, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, componentwise transport, continuation replay, provenance, and local naming. It receives no selected limit, quotient filter, countable-choice schedule, host equality, ambient $\RealUp$ completeness theorem, Lean verification row, or bridge certificate.
\end{theorem}
\begin{proof}
Begin with a completion-facing or $\RealUp$-facing read named by $P$. Carrier projection restricts the consumer to the rows displayed in \autoref{def:cauchy-filter-modulus-carrier}.

Apply \autoref{thm:cauchy-filter-modulus-regular-readback}. The precision request must pass through $F,B,G,S,D,R$ before a regular rational readback is available.

The seal row $E$ is placed after that regular readback route. A consumer therefore sees the terminal $\RealUp$ boundary only after the source filter, basis witness, regularity row, finite windows, dyadic ledger, and regular rational handoff have all been replayed.

The structural rows do not add analytic content. The transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$ preserve and name the displayed route, so selected limits, quotient filters, choice schedules, host equality, ambient real completeness, Lean verification, and bridge checking cannot enter through the seal boundary.
\end{proof}

\begin{closurestatus}{\CauchyFilterModulusUp}
  \constructivestory{A $\CauchyFilterModulusUp$ packet is generated from a CauchyFilter source row, a CauchyFilterBasis row, a RegularCauchyFilter regularity row, StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a RealUp seal boundary, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-filter-modulus-carrier}, \autoref{thm:cauchy-filter-modulus-namecert-obligations}, \autoref{thm:cauchy-filter-modulus-regular-readback}, and \autoref{thm:cauchy-filter-modulus-real-handoff} seed the finite modulus interface from Cauchy-filter evidence and basis requests to regular rational readback before the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient filters, countable choice, host equality, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, source-to-basis routing, regular filter modulus extraction, window and dyadic replay, regular readback, Real handoff, transport, replay, provenance, and local naming for BEDC.Derived.CauchyFilterModulusUp.}
\end{closurestatus}
