\chapter{A Concrete Naming Certificate for $\RealityConstrainedScientificMethodologyUp$}
\label{ch:concrete-instances-reality-constrained-scientific-methodology-namecert}
\origin{ai}

The $\RealityConstrainedScientificMethodologyUp$ packet realizes the methodology consequences of \autoref{ch:visions-reality-constrained-scientific-methodology} as one finite NameCert carrier. It sits after the methodology ledger of \autoref{ch:concrete-instances-reality-constrained-methodology-ledger-namecert}, the physical model audit of \autoref{ch:concrete-instances-physical-model-audit-namecert}, the explanation packet of \autoref{ch:concrete-instances-reality-constrained-explanation-namecert}, and the idealization residue seal of \autoref{ch:concrete-instances-scientific-idealization-residue-seal-namecert}. Those siblings expose ledger, audit, explanation, and idealization rows separately; this carrier binds them with an effective-domain row, a domain-leakage failure surface, audit routing, provenance, and a local name before a scientific-methodology claim may be read as accepted.

\begin{definition}[Reality-constrained scientific-methodology carrier]
\label{def:reality-constrained-scientific-methodology-carrier}
A $\RealityConstrainedScientificMethodologyUp$ carrier is a finite $\BHist$ packet
$$
M=(X,A,E,I,D,L,F,R,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the methodology-ledger row inherited from $\RealityConstrainedMethodologyLedgerUp$, naming scope, domain-leakage refusals, extension routes, and failure records.
\item $A$ is the physical-model-audit row inherited from $\PhysicalModelAuditUp$, naming source traces, observed signatures, model signatures, comparison, tower, stability, descent, ledger, failure, and strength rows.
\item $E$ is the explanation-certificate row inherited from $\RealityConstrainedExplanationUp$, naming observation bundle, model, phenomenon, signature comparison, descent, residue, and failure surface.
\item $I$ is the idealization-residue row inherited from $\ScientificIdealizationResidueSealUp$, naming the idealization arrow, removed source material, descent row, failure surface, and safe scope.
\item $D$ is the effective-domain row, naming the observation bundle, tower region, admissible consumers, and physical-signature interface over which the methodology packet is licensed.
\item $L$ is the domain-leakage row, naming attempted exports beyond $D$ and the finite refusal or routing record for each attempted export.
\item $F$ is the methodology failure-surface row, collecting explanation failure, audit mismatch, active idealization residue, domain leakage, and open physical-fit defeat.
\item $R$ is the audit-route row, recording how a consumer reaches the accepted methodology read through explanation, audit, idealization, domain, leakage, and failure rows.
\item $T$ records componentwise $\hsame$ transport for $X,A,E,I,D,L,F,R,C,P,N$.
\item $C$ records displayed $\Cont$ replay of the accepted methodology route.
\item $P$ records $\Pkg$ provenance over the sibling carriers, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RealityConstrainedScientificMethodologyUp}$ row.
\end{enumerate}
The carrier has no coordinate for bare explanatory syntax, detached model truth, global realism, unledgered idealization, unbounded effective exactness, or methodology export outside the displayed packet.
\end{definition}
\leanchecked{BEDC.Derived.RealityConstrainedScientificMethodologyUp.TasteGate.RealityConstrainedScientificMethodologyTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Reality-constrained scientific-methodology obligation surface]
\label{thm:reality-constrained-scientific-methodology-obligation-surface}
For the carrier of \autoref{def:reality-constrained-scientific-methodology-carrier}, the local $\NameCert_{\RealityConstrainedScientificMethodologyUp}$ surface consists exactly of six obligation rows:
\begin{enumerate}
\item carrier admission: the accepted object is exactly $M=(X,A,E,I,D,L,F,R,T,C,P,N)$;
\item explanation accountability: explanation-to-truth-cert consumers must pass through the explanation row $E$ and its residue and failure surface;
\item audit accountability: physical-model reads must pass through $A$ and the accepted audit route;
\item idealization accountability: ideal endpoint reads must pass through the idealization residue row $I$;
\item domain-leakage accountability: every export beyond the effective-domain row $D$ must be recorded in $L$ and exposed to $F$;
\item route and naming accountability: accepted consumers must preserve $R,T,C,P,N$ as the audit route, componentwise transport, replay, provenance, and local name of the same packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:reality-constrained-scientific-methodology-carrier}. The packet lists the only rows available to the local methodology certificate.

Explanation accountability is carried by $E$. A consumer that reads explanation toward truth without the observation, model, phenomenon, signature comparison, descent, residue, and failure-surface material of $E$ has not passed through the accepted explanation certificate.

Audit and idealization accountability are carried by $A$ and $I$. The audit row records the finite physical-model comparison and its strength, while the idealization row records the ideal endpoint together with residue, descent, failure, and scope.

Domain-leakage accountability is carried by $D,L,F$. The effective-domain row names the licensed region, the leakage row records attempted exports beyond it, and the failure surface makes those refusals visible to the consumer.

Finally $R,T,C,P,N$ preserve the same displayed route. Since the carrier contains no further coordinate, a methodology consumer cannot bypass explanation, audit, idealization residue, domain leakage, or local naming while remaining an accepted $\RealityConstrainedScientificMethodologyUp$ read.
\end{proof}

\begin{theorem}[Reality-constrained scientific-methodology consumer factorization]
\label{thm:reality-constrained-scientific-methodology-consumer-factorization}
Every accepted explanation-to-truth-cert consumer of a $\RealityConstrainedScientificMethodologyUp$ packet factors through either the explanation certificate row $E$ or the idealization residue row $I$, and in both cases preserves the effective-domain row $D$, leakage row $L$, failure surface $F$, audit route $R$, transport $T$, replay $C$, provenance $P$, and local name $N$.
\end{theorem}
\begin{proof}
Read the obligation surface of \autoref{thm:reality-constrained-scientific-methodology-obligation-surface}. An explanation-to-truth-cert consumer is admitted only when explanation accountability or idealization accountability is displayed.

In the explanation branch, the route uses $E$ and therefore carries the observation bundle, model row, phenomenon row, signature comparison, descent, residue, and failure surface. In the idealization branch, the route uses $I$ and therefore carries the idealization arrow, residue ledger, descent, failure surface, and safe scope.

Both branches still belong to the same methodology packet. The domain, leakage, failure, audit-route, transport, replay, provenance, and local-name rows $D,L,F,R,T,C,P,N$ remain visible, so neither branch can become a detached truth-cert consumer.
\end{proof}

\falsifiablePrediction{If the methodology packet is atomic, then every accepted explanation-to-truth-cert consumer must factor through either the explanation certificate row or the idealization residue row; a consumer bypassing both refutes the chapter.}

\independenceWitness{realityconstrainedmethodologyledger, physicalmodelaudit, realityconstrainedexplanation, scientificidealizationresidueseal, openphysicalfit: the methodology carrier has both explanation and idealization-residue rows plus a domain-leakage failure surface, while each sibling omits at least one of those rows, so no row-preserving bijection can identify the carriers.}

\closureat{RealityConstrainedScientificMethodologyUp}{seedStr}
\closureat{RealityConstrainedScientificMethodologyUp}{obligationStr}[BEDC.Derived.RealityConstrainedScientificMethodologyUp.TasteGate.RealityConstrainedScientificMethodologyTasteGate\_single\_carrier\_alignment]

\begin{closurestatus}{\RealityConstrainedScientificMethodologyUp}
  \constructivestory{A $\RealityConstrainedScientificMethodologyUp$ packet is generated from methodology-ledger, physical-audit, explanation, idealization-residue, effective-domain, domain-leakage, failure-surface, audit-route, transport, replay, provenance, and local NameCert rows.}
  \leanchecked{BEDC.Derived.RealityConstrainedScientificMethodologyUp.taste\_gate}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:reality-constrained-scientific-methodology-carrier}, \autoref{thm:reality-constrained-scientific-methodology-obligation-surface}, and \autoref{thm:reality-constrained-scientific-methodology-consumer-factorization} bind the finite carrier, obligation surface, and explanation-or-idealization consumer factorization.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.RealityConstrainedScientificMethodologyUp.TasteGate.RealityConstrainedScientificMethodologyTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not assert global model truth, unbounded realism, final empirical closure, public closure, or bridge checking for $\RealityConstrainedScientificMethodologyUp$.}
  \upgradepath{Scoped closure requires downstream examples showing that truth-cert and open-fit consumers preserve the explanation-or-idealization factorization through the displayed domain-leakage surface.}
\end{closurestatus}
