\chapter{A Concrete Naming Certificate for $\SigmaAlgebraUp$}
\label{ch:concrete-instances-sigma-algebra-namecert}
\origin{human}

Following Kolmogorov and Caratheodory measure theory, the $\SigmaAlgebraUp$ packet records the measurable-event closure surface that measure and probability chapters read before assigning values to events. It sits between the displayed event-family rows of \autoref{ch:concrete-instances-measure-namecert}, the probability carrier of \autoref{ch:concrete-instances-probspace-namecert}, the measurable-preimage discipline of \autoref{ch:concrete-instances-randomvar-namecert}, and the pushforward readback of \autoref{ch:concrete-instances-distribution-namecert}. The packet names finite BEDC rows for event admission, complement, and countable-union schedules; it is not a host powerset, completed measurable universe, quotient event algebra, countable-choice selector, or ambient measure object.

\begin{definition}[Sigma-algebra carrier]
\label{def:sigma-algebra-carrier}
A $\SigmaAlgebraUp$ carrier is a finite $\BHist$ packet
$$
S=(E,Q,Z,K,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the event-family row, listing the measurable-event entries visible to downstream $\MeasureUp$ and $\ProbSpaceUp$ consumers.
\item $Q$ is the classifier row, comparing displayed events only through the local event-family equivalence and its transported $\hsame$ witnesses.
\item $Z$ is the empty-event row, recording the admitted empty event and its classifier readback.
\item $K$ is the complement row, assigning to every displayed event a displayed complement event over the same family row.
\item $U$ is the countable-union schedule, naming a displayed union event for every displayed countable event schedule that the packet admits.
\item $H$ records componentwise $\hsame$ transport for the event family, classifier, empty-event, complement, countable-union, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an event request through $E,Q,Z,K,U$ and then to the structural rows.
\item $P$ is the $\Pkg$ provenance over $\SigmaAlgebraUp$, $\MeasureUp$, $\ProbSpaceUp$, $\RandomVarUp$, $\DistributionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SigmaAlgebraUp}$ row.
\end{enumerate}
The carrier has no coordinate for host powersets, completed sigma-algebras, quotient event equality, countable-choice selection, ambient measures, or external measurable-space instances.
\end{definition}

\begin{theorem}[Sigma-algebra NameCert obligations]
\label{thm:sigma-algebra-namecert-obligations}
For every accepted $\SigmaAlgebraUp$ carrier $S=(E,Q,Z,K,U,H,C,P,N)$, the local $\NameCert_{\SigmaAlgebraUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item event-family admission, requiring $E$ before any measurable-event read is public;
\item classifier stability, requiring $Q$ and componentwise $\hsame$ transport through $H$ to preserve displayed event comparison;
\item empty-event admission, requiring $Z$ to identify the empty event inside the same event family;
\item complement and countable-union closure, requiring $K$ and $U$ to supply displayed closure rows before a downstream $\MeasureUp$ or $\ProbSpaceUp$ consumer may cite sigma-algebra structure;
\item provenance and local naming, requiring $C,P,N$ to replay, source, and name only the displayed packet, with no host powerset, completed sigma-algebra, quotient event algebra, countable-choice selector, ambient measure, or external measurable-space coordinate.
\end{enumerate}
No local sigma-algebra obligation is stored outside $E,Q,Z,K,U,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:sigma-algebra-carrier}. The event-family row $E$ is the only source of measurable events, and the classifier row $Q$ is the only public comparison between them.

The empty-event row $Z$, complement row $K$, and countable-union schedule $U$ supply the closure operations in the same displayed family. Thus a closure request cannot leave the carrier to inspect a host powerset or completed measurable universe.

Transport and replay are componentwise through $H$ and $C$. These rows preserve the event-family, classifier, empty-event, complement, and countable-union data without adding a second equality or a selected representative.

Finally $P$ and $N$ source and name precisely this packet. Since the forbidden host and quotient coordinates are absent, the five listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Sigma-algebra measure handoff]
\label{thm:sigma-algebra-measure-handoff}
Every $\MeasureUp$, $\ProbSpaceUp$, $\RandomVarUp$, or $\DistributionUp$ consumer that cites measurable-event structure from an accepted $\SigmaAlgebraUp$ carrier $S=(E,Q,Z,K,U,H,C,P,N)$ receives only the displayed event-family row $E$, classifier row $Q$, empty-event row $Z$, complement row $K$, countable-union schedule $U$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local $\NameCert$ naming through $N$. The handoff exports no host powerset, completed sigma-algebra, quotient event algebra, countable-choice selector, ambient measure, or external measurable-space instance.
\end{theorem}
\begin{proof}
Read \autoref{thm:sigma-algebra-namecert-obligations}. A downstream consumer must first consume the event-family, classifier, empty-event, complement, and countable-union rows before treating the packet as sigma-algebra structure.

For $\MeasureUp$ and $\ProbSpaceUp$, these rows provide the measurable-event surface before any value or probability row can be read. For $\RandomVarUp$ and $\DistributionUp$, the same rows are the source and target event families through which measurable preimages and pushforward events are routed.

The rows $H,C,P,N$ preserve, replay, source, and name the handoff. Because the carrier has no host powerset, completed sigma-algebra, quotient event algebra, countable-choice selector, ambient measure, or external measurable-space coordinate, the listed rows are the whole exported interface.
\end{proof}

\closureat{SigmaAlgebraUp}{seedStr}

\begin{closurestatus}{\SigmaAlgebraUp}
  \constructivestory{A $\SigmaAlgebraUp$ packet is generated from a displayed event-family row, local event classifier, empty-event row, complement row, countable-union schedule, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:sigma-algebra-carrier}, \autoref{thm:sigma-algebra-namecert-obligations}, and \autoref{thm:sigma-algebra-measure-handoff} seed the finite measurable-event closure surface consumed by MeasureUp, ProbSpaceUp, RandomVarUp, and DistributionUp rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host powersets, completed sigma-algebras, quotient event equality, countable-choice selection, ambient measure objects, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked event-family admission, classifier stability, empty-event admission, complement closure, countable-union closure, transport, replay, provenance, and local naming for BEDC.Derived.SigmaAlgebraUp.}
\end{closurestatus}
