\chapter{A Concrete Naming Certificate for $\BishopIntervalNetExtractionUp$}
\label{ch:concrete-instances-bishop-interval-net-extraction-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, 1985, the $\BishopIntervalNetExtractionUp$ packet records explicit finite $\varepsilon$-net extraction for a located closed interval before the L10 Real and Completion route consumes compactness-like data. It sits after the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the interval finite-net surface of \autoref{ch:concrete-instances-located-closed-interval-finite-net-namecert}, the total-bounded interval surface of \autoref{ch:concrete-instances-closed-interval-total-bounded-namecert}, the compact real-interval packet of \autoref{ch:concrete-instances-compact-real-interval-namecert}, and the located Cauchy bracket route of \autoref{ch:concrete-instances-located-cauchy-bracket-namecert}. The packet names only displayed endpoints, tolerance requests, finite net rows, stream windows, regular readback, Real seals, transport, replay, provenance, and local naming; it is not an open-cover compactness theorem, host interval primitive, quotient-real equality, trichotomy oracle, or ambient completeness principle.

\begin{definition}[Bishop interval net extraction carrier]
\label{def:bishop-interval-net-extraction}
A $\BishopIntervalNetExtractionUp$ carrier is a finite $\BHist$ packet
$$
I=(A,B,\varepsilon,D,G,W,R,E,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the located closed interval endpoint rows, read through $\DyadicRatCoreUp$ rational brackets and the surrounding $\RealUp$ seals.
\item $\varepsilon$ is the positive tolerance request row, stored as a dyadic radius budget rather than as a host real inequality.
\item $D$ is the dyadic subdivision ledger, recording the integer step count, endpoint refinements, successor grid positions, and comparison witnesses used to keep adjacent grid rows within the requested tolerance.
\item $G$ is the finite grid-net row, a displayed list of dyadic points between $A$ and $B$ whose coverage ledger is inherited by $\LocatedClosedIntervalFiniteNetUp$ and $\ClosedIntervalTotalBoundedUp$ consumers.
\item $W$ is the finite $\StreamNameUp$ observation-window row used to inspect the endpoint and grid requests without selecting an infinite stream representative.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same finite windows and dyadic subdivision budget.
\item $E$ is the terminal $\RealUp$ seal row for endpoint, grid-point, and coverage reads, reached only after $A,B,\varepsilon,D,G,W,R$ have been displayed.
\item $F$ is the compact-interval handoff row, routing the extracted finite net to $\CompactRealIntervalUp$ through the interval finite-net and total-bounded sibling packets.
\item $H$ records componentwise $\hsame$ transport for $A,B,\varepsilon,D,G,W,R,E,F$ and the local naming row.
\item $C$ records displayed $\Cont$ replay from a tolerance request through endpoint brackets, dyadic subdivision, grid formation, finite stream windows, regular readback, Real seals, and the compact-interval handoff.
\item $P$ is the $\Pkg$ provenance over $\BishopIntervalNetExtractionUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\LocatedClosedIntervalFiniteNetUp$, $\ClosedIntervalTotalBoundedUp$, $\CompactRealIntervalUp$, $\LocatedCauchyBracketUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopIntervalNetExtractionUp}$ row.
\end{enumerate}
The classifier compares accepted interval-net packets only through $A,B,\varepsilon,D,G,W,R,E,F,H,C,P,N$. It has no coordinate for an open-cover subcover, a host interval primitive, quotient real equality, trichotomy, countable choice, a selected limiting point, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop interval net extraction NameCert obligations]
\label{thm:bishop-interval-net-extraction-namecert}
For every accepted $\BishopIntervalNetExtractionUp$ carrier
$$
I=(A,B,\varepsilon,D,G,W,R,E,F,H,C,P,N),
$$
the local $\NameCert_{\BishopIntervalNetExtractionUp}$ surface consists exactly of located endpoint admission, positive tolerance admission, dyadic subdivision formation, finite grid-net coverage, finite $\StreamNameUp$ inspection, $\RegSeqRatUp$ readback, terminal $\RealUp$ seal handoff, compact-interval routing through the located finite-net and total-bounded sibling packets, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier rows. The endpoints $A,B$ and tolerance row $\varepsilon$ are the only analytic inputs, and both are read through displayed dyadic and Real-seal data rather than through a host interval primitive.

The subdivision ledger $D$ forms a finite dyadic grid by repeated successor steps over the displayed endpoint brackets. The grid row $G$ records the resulting finite list and its interval coverage ledger, so every coverage read is finite before any compactness-facing handoff is available.

The readback rows $W$ and $R$ keep endpoint and grid inspection inside finite $\StreamNameUp$ windows and $\RegSeqRatUp$ rational observations. The terminal seal row $E$ is downstream of those rows, so Real-facing consumers cannot bypass the dyadic grid by selecting quotient representatives or host limits.

Finally $F,H,C,P,N$ route the same finite net to $\LocatedClosedIntervalFiniteNetUp$, $\ClosedIntervalTotalBoundedUp$, and $\CompactRealIntervalUp$ consumers while preserving transport, replay, provenance, and local naming. Since the carrier has no coordinate for open-cover compactness, host interval primitives, quotient real equality, trichotomy, countable choice, selected limits, or ambient completeness, the listed rows exhaust the NameCert obligations.
\end{proof}

\closureat{BishopIntervalNetExtractionUp}{seedStr}

\begin{closurestatus}{\BishopIntervalNetExtractionUp}
  \constructivestory{A $\BishopIntervalNetExtractionUp$ packet is generated from located closed interval endpoints, a positive dyadic tolerance request, a dyadic subdivision ledger, finite grid-net coverage, finite StreamName windows, RegSeqRat readback, RealUp seals, compact-interval handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-interval-net-extraction} and \autoref{thm:bishop-interval-net-extraction-namecert} seed the explicit finite interval-net extraction packet for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, host real equality, quotient interval equality, trichotomy, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked endpoint admission, positive tolerance admission, dyadic subdivision formation, finite grid coverage, finite-window readback, RealUp seal handoff, compact-interval routing, transport, replay, provenance, and local naming for BEDC.Derived.BishopIntervalNetExtractionUp.}
\end{closurestatus}
