\chapter{A Concrete Naming Certificate for $\CandidateMediatedSNUp$}
\label{ch:concrete-instances-candidate-mediated-sn-namecert}
\origin{ai}

The $\CandidateMediatedSNUp$ packet realizes the candidate-mediated branch of \autoref{ch:metacic-normalization-audit-map} as finite NameCert data. It reads the sibling MetaCIC sources \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, and \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert} as route anchors, while keeping candidate evidence explicit before any strong-normalization conclusion is exported. The packet is a normalization-evidence landing, not a blanket theorem that every closed typed MetaCIC term is strongly normalizing without displayed candidate data.

\begin{definition}[Candidate-mediated strong-normalization carrier]
\label{def:candidate-mediated-sn-carrier}
A $\CandidateMediatedSNUp$ carrier is a finite $\BHist$ packet
$$
M=(T,E,C,S,A,NF,O,R,H,Q,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the closed typed MetaCIC term row consumed by the endpoint projection.
\item $E$ is the candidate-evidence row, allowing Candidate, ClosedCandidate, or CandidateSet membership evidence to be named without erasure.
\item $C$ is the candidate-closure row, recording the closure and beta-stability data needed by the candidate route.
\item $S$ is the strong-normalization export row downstream of $E$ and $C$.
\item $A$ is the Pi/application adequacy row, keeping function and argument reads inside the same candidate-mediated interface.
\item $NF$ is the no-infinite-reduction projection row obtained from the same strong-normalization evidence.
\item $O$ is the obstruction row naming subject-reduction, substitution, confluence, and closed-consistency boundaries that remain outside this packet.
\item $R$ is the frontier route row, reading $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICConfluenceAuditPacketUp$, and $\NormalFormConsistencySealUp$ as named sources rather than replacing them.
\item $H$ records componentwise $\hsame$ transport for the typed term, candidate evidence, closure, strong-normalization export, adequacy, no-infinite-reduction projection, obstruction, route, replay, provenance, and local naming rows.
\item $Q$ records displayed $\Cont$ replay from candidate evidence to the strong-normalization and no-infinite-reduction endpoint rows.
\item $P$ is the $\Pkg$ provenance over $\CandidateMediatedSNUp$, \autoref{ch:metacic-normalization-audit-map}, \autoref{ch:concrete-instances-metaciccriticalpath-namecert}, \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, \autoref{ch:concrete-instances-metacic-confluence-audit-packet-namecert}, \autoref{ch:concrete-instances-normal-form-consistency-seal-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CandidateMediatedSNUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,E,C,S,A,NF,O,R,H,Q,P,N$.
\end{definition}

\begin{theorem}[Candidate-mediated strong-normalization NameCert obligations]
\label{thm:candidate-mediated-sn-namecert-obligations}
For every accepted $\CandidateMediatedSNUp$ carrier
$$
M=(T,E,C,S,A,NF,O,R,H,Q,P,N),
$$
the local $\NameCert_{\CandidateMediatedSNUp}$ surface consists exactly of closed typed term admission through $T$, candidate evidence through $E$, candidate closure through $C$, strong-normalization export through $S$, Pi/application adequacy through $A$, no-infinite-reduction projection through $NF$, obstruction visibility through $O$, route anchoring through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $Q$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:candidate-mediated-sn-carrier}. The closed typed term row $T$ names the endpoint shape, but it does not carry strong normalization on its own.

The evidence rows $E$ and $C$ are the positive source. The export row $S$ and no-infinite-reduction row $NF$ are downstream of that source, while $A$ keeps Pi and application reads inside the candidate-mediated route.

The obstruction and route rows are also part of the certificate. They expose the critical-path, normalization-frontier, confluence-audit, and normal-form-consistency boundaries rather than silently converting them into unconditional normalization.

Finally $H,Q,P,N$ provide transport, replay, provenance, and local naming. Since no carrier coordinate stores an evidence-free closed-term strong-normalization theorem, the listed rows exhaust the packet.
\end{proof}

\begin{theorem}[Candidate-mediated strong-normalization frontier handoff]
\label{thm:candidate-mediated-sn-frontier-handoff}
Every strong-normalization read exported by an accepted $\CandidateMediatedSNUp$ packet factors through displayed candidate evidence before it reaches a closed typed term endpoint. The route may cite $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICConfluenceAuditPacketUp$, and $\NormalFormConsistencySealUp$ as sibling anchors, but it cannot erase the Candidate, ClosedCandidate, or CandidateSet evidence row into a global closed-term normalization theorem.
\end{theorem}
\begin{proof}
Use \autoref{thm:candidate-mediated-sn-namecert-obligations}. The endpoint row $T$ is read only after the evidence and closure rows have been opened.

The adequacy and no-infinite-reduction rows are not independent endpoints. They are downstream projections of the same candidate-mediated source, so application, Pi, and infinite-reduction reads remain attached to $E$ and $C$.

The sibling route row $R$ records where the public MetaCIC boundaries are read. It preserves the normalization frontier and confluence audit as named sources, and therefore blocks the evidence-free closed-term claim.
\end{proof}

\begin{theorem}[Candidate-mediated SN has no hidden oracle]
\label{thm:candidate-mediated-sn-no-hidden-oracle}
Every StrongNormalizable row exported by an accepted $\CandidateMediatedSNUp$ packet factors through one of the displayed Candidate, ClosedCandidate, or CandidateSet evidence rows named by the carrier. If no such evidence row is displayed, the packet exports only the boundary ledger over $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICConfluenceAuditPacketUp$, and $\NormalFormConsistencySealUp$, and it exports no blanket strong-normalization conclusion for all closed typed MetaCIC terms.
\end{theorem}
\begin{proof}
Read the packet through the normalization audit map and then project the carrier of \autoref{def:candidate-mediated-sn-carrier}. The only positive normalization source in the carrier is the evidence pair $E,C$, where $E$ names Candidate, ClosedCandidate, or CandidateSet membership and $C$ records the closure data needed by that evidence.

The exported strong-normalization row $S$ and the no-infinite-reduction row $NF$ sit downstream of those displayed rows. Thus any StrongNormalizable export must pass through the candidate evidence before it reaches the closed typed term row $T$.

If the candidate evidence is absent, the remaining visible rows are obstruction, route, transport, replay, provenance, and local naming. They preserve the MetaCIC boundary ledger and the sibling audit sources, but they contain no coordinate from which an evidence-free closed-term strong-normalization theorem can be read.
\end{proof}

\begin{theorem}[Candidate-mediated obstruction frontier]
\label{thm:candidate-mediated-sn-obstruction-frontier}
Every public strong-normalization or no-infinite-reduction read exported by an accepted $\CandidateMediatedSNUp$ carrier
$$
M=(T,E,C,S,A,NF,O,R,H,Q,P,N)
$$
must pass through the candidate-evidence row $E$ and candidate-closure row $C$ before it reaches $S$ or $NF$. The route must also retain the obstruction row $O$, naming subject-reduction, substitution, confluence, and closed-consistency boundaries, and it must preserve $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICConfluenceAuditPacketUp$, and $\NormalFormConsistencySealUp$ as route boundaries rather than replacement theorems.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:candidate-mediated-sn-carrier}. The endpoint row $T$ is not an evidence-free normalization theorem; the positive route begins with $E$ and $C$ and only then reaches the strong-normalization and no-infinite-reduction rows $S$ and $NF$.

Apply \autoref{thm:candidate-mediated-sn-namecert-obligations}. Its obstruction-visibility and route-anchoring clauses keep $O$ and $R$ inside the local certificate, so subject reduction, substitution, confluence, and closed consistency remain named boundaries.

Now use \autoref{thm:candidate-mediated-sn-frontier-handoff}. The handoff prevents Candidate, ClosedCandidate, or CandidateSet evidence from being erased into a global closed-term claim.

The rows $H,Q,P,N$ transport, replay, source, and name the same route. Thus $\MetaCICCriticalPathUp$, $\MetaCICNormalizationFrontierUp$, $\MetaCICConfluenceAuditPacketUp$, and $\NormalFormConsistencySealUp$ are preserved as sibling boundaries, while $S$ and $NF$ remain candidate-mediated exports downstream of $E$ and $C$.
\end{proof}

\begin{theorem}[Candidate-mediated strong-normalization TasteGate obligation]
\label{thm:candidate-mediated-sn-tastegate-obligation}
Future Lean support for $\CandidateMediatedSNUp$ requires TasteGate $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances. Nontriviality must distinguish an accepted packet with displayed candidate evidence from a closed typed term row without that evidence, and field faithfulness must preserve the row order
$$
T \longmapsto E \longmapsto C \longmapsto S \longmapsto A \longmapsto NF \longmapsto O \longmapsto R \longmapsto H,Q,P,N
$$
before any carrier-alignment theorem can serve as a checked realization.
\end{theorem}
\begin{proof}
Nontriviality follows from the carrier boundary. Removing $E$ or $C$ leaves the closed typed term endpoint without the evidence route that supplies strong normalization.

Field faithfulness is the row-order condition. If a TasteGate projection permutes or erases $E,C,S,A,NF,O,R,H,Q,P,N$, the packet no longer represents the candidate-mediated route named by \autoref{def:candidate-mediated-sn-carrier}.
\end{proof}

\falsifiablePrediction{Every accepted $\CandidateMediatedSNUp$ strong-normalization read exposes candidate evidence before the endpoint: closed typed term row first, candidate evidence second, candidate closure third, strong-normalization export fourth, Pi/application adequacy fifth, no-infinite-reduction projection sixth, and obstruction, route, transport, replay, provenance, and local naming rows thereafter.}

\independenceWitness{metacic-normalization-audit-map, metacic-critical-path, metacic-normalization-frontier, metacic-confluence-audit-packet, normal-form-consistency-seal: $\CandidateMediatedSNUp$ is not bijective to any listed source because it isolates the evidence-carrying strong-normalization route while preserving each sibling as a named boundary rather than a replacement theorem.}

\closureat{CandidateMediatedSNUp}{seedStr}

\begin{closurestatus}{\CandidateMediatedSNUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:candidate-mediated-sn-carrier}, \autoref{thm:candidate-mediated-sn-namecert-obligations}, \autoref{thm:candidate-mediated-sn-frontier-handoff}, and \autoref{thm:candidate-mediated-sn-tastegate-obligation} seed the candidate-mediated strong-normalization evidence route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close unconditional strong normalization for every closed typed MetaCIC term, subject reduction, arbitrary substitution preservation, global confluence, closed consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, candidate-evidence visibility, candidate-closure stability, strong-normalization export, Pi/application adequacy routing, no-infinite-reduction projection, obstruction visibility, TasteGate nontriviality, field faithfulness, transport, replay, provenance, and local naming for BEDC.Derived.CandidateMediatedSNUp.}
  \constructivestory{A $\CandidateMediatedSNUp$ packet is generated from a closed typed term row, candidate evidence, candidate closure, strong-normalization export, Pi/application adequacy rows, no-infinite-reduction projection, obstruction boundaries, sibling route anchors, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
