\chapter{A Concrete Naming Certificate for $\CompactMetricHyperspaceUp$}
\label{ch:concrete-instances-compact-metric-hyperspace-namecert}
\origin{human}

Following Hausdorff, Vietoris, and Kelley, the $\CompactMetricHyperspaceUp$ packet records the recognized hyperspace of nonempty compact subsets of a compact metric BEDC source as finite Hausdorff-distance and Vietoris-window data. It refines the compact-subset carrier of \autoref{ch:concrete-instances-hyperspace-namecert} by requiring the source rows of \autoref{ch:concrete-instances-compactmetric-namecert}, \autoref{ch:concrete-instances-metric-namecert}, \autoref{ch:concrete-instances-totallybounded-namecert}, and \autoref{ch:concrete-instances-completemetric-namecert} to be displayed before any hyperspace consumer reads compact-subset convergence, finite nets, or Hausdorff tolerances.

\begin{definition}[Compact metric hyperspace carrier]
\label{def:compact-metric-hyperspace-carrier}
A $\CompactMetricHyperspaceUp$ carrier is a finite $\BHist$ packet
$$
K=(X,H,F,D,V,L,T,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the compact metric source row, including the $\MetricUp$ distance witnesses, $\TotallyBoundedUp$ finite-net schedule, and $\CompleteMetricUp$ Cauchy-limit boundary carried by $\CompactMetricUp$.
\item $H$ is the underlying $\HyperspaceUp$ compact-subset ledger over $X$, with compact-subset presentations inspected only through the displayed source rows.
\item $F$ is the finite nonempty subset-window family: each window records a positive tolerance, a finite source-net list, and the compact-subset names covered at that tolerance.
\item $D$ is the bidirectional Hausdorff-distance readback ledger for pairs of displayed compact-subset names, routed through the finite windows in $F$ and the source metric row in $X$.
\item $V$ is the Vietoris finite-net scope row, recording the finite hit-and-miss windows whose opens are represented by metric balls and finite complements read from $X$.
\item $L$ is the Hausdorff-completion route row: a Cauchy family of compact-subset names is read through $D$ and lands back in a compact-subset row of $H$ by the total-bounded and complete source data.
\item $T$ records componentwise $\hsame$ transport for $X,H,F,D,V,L,P,N$.
\item $C$ records displayed $\Cont$ replay through
$$
X,H,F,D,V \longmapsto L .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactMetricHyperspaceUp$, $\HyperspaceUp$, $\CompactMetricUp$, $\MetricUp$, $\TotallyBoundedUp$, $\CompleteMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactMetricHyperspaceUp}$ row.
\end{enumerate}
The carrier has no coordinate for host powersets, quotient compacta, open-cover compactness, selected limits, or choice-selected representatives.
\end{definition}

\begin{theorem}[Compact metric hyperspace NameCert obligations]
\label{thm:compact-metric-hyperspace-namecert-obligations}
For every accepted $\CompactMetricHyperspaceUp$ carrier
$$
K=(X,H,F,D,V,L,T,C,P,N),
$$
the local $\NameCert_{\CompactMetricHyperspaceUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item compact metric source admission for $X$, requiring the displayed $\MetricUp$, $\TotallyBoundedUp$, and $\CompleteMetricUp$ rows carried by $\CompactMetricUp$;
\item hyperspace-subset admission for $H$, requiring every compact-subset name to be read through \autoref{ch:concrete-instances-hyperspace-namecert};
\item finite Hausdorff-window admission for $F$ and $D$, requiring two directed finite coverage reads before a Hausdorff tolerance is public;
\item Vietoris finite-net scope for $V$, requiring hit-and-miss data to be represented by finitely many source metric balls and finite complement checks;
\item completion-route stability for $L,T,C$, requiring Cauchy hyperspace reads to replay through the compact source finite nets and complete boundary;
\item provenance and name exhaustion for $P,N$, excluding host powersets, quotient compacta, open-cover compactness, selected limits, and choice-selected representatives.
\end{enumerate}
No local NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:compact-metric-hyperspace-carrier}. The source row $X$ is the only place where metric distance, finite nets, and Cauchy-limit service enter the packet.

The hyperspace-subset obligation is exactly the row $H$. The finite-window and Hausdorff obligations are exactly $F$ and $D$, so every compact-subset comparison uses displayed finite source data rather than an ambient set of compacta.

The Vietoris obligation is the row $V$. Its hit-and-miss windows are finite metric-ball inspections over $X$, hence they remain synchronized with the Hausdorff ledger instead of importing open-cover compactness.

Finally $L,T,C,P,N$ close the route under completion readback, componentwise transport, replay, provenance, and local naming. Since the carrier has no further coordinates, the six listed rows exhaust the local naming surface.
\end{proof}

\begin{theorem}[Compact metric hyperspace Hausdorff completion route]
\label{thm:compact-metric-hyperspace-hausdorff-completion-route}
Every accepted $\CompactMetricHyperspaceUp$ carrier routes Hausdorff-Cauchy compact-subset data through the displayed $\CompactMetricUp$ source finite nets and $\CompleteMetricUp$ boundary. A Cauchy request in the hyperspace reads only the rows $H,F,D,L,T,C,P,N$, and the resulting compact-subset landing row is again a displayed $\HyperspaceUp$ name over the same source $X$.
\end{theorem}
\begin{proof}
Begin with the Hausdorff ledger $D$. Each directed coverage read cites a finite source-net window from $F$ and a source distance witness from $X$.

The Cauchy request is then consumed by $L$. Total boundedness supplies finite source windows at each requested tolerance, and completeness supplies the source boundary needed to keep the compact-subset landing row inside the same compact metric packet.

Transport and replay are handled by $T$ and $C$. These rows carry the compact metric source, hyperspace rows, finite windows, Hausdorff ledger, and landing row together, so the route cannot leave the displayed carrier.

The provenance and local name rows $P,N$ certify that no selected limit object, quotient compactum, or host powerset is exported. The landing row is therefore a $\HyperspaceUp$ name over $X$ rather than an external compactum.
\end{proof}

\begin{theorem}[Compact metric hyperspace Vietoris finite-net scope]
\label{thm:compact-metric-hyperspace-vietoris-finite-net-scope}
The Vietoris reading of an accepted $\CompactMetricHyperspaceUp$ carrier is confined to the finite hit-and-miss windows in $V$. Each hit row names a finite family of source metric balls meeting the displayed compact-subset row, each miss row names a finite complement check against the same source net, and the read is stable under the componentwise transport $T$ and replay $C$.
\end{theorem}
\begin{proof}
Project the row $V$. Its data are finite hit-and-miss windows, and each window is represented by source metric balls and finite complement checks over $X$.

The row $H$ supplies the compact-subset names being inspected. The rows $F$ and $D$ synchronize those names with Hausdorff finite-net reads, so the Vietoris view cannot inspect a larger host topology.

Stability follows from $T$ and $C$. Componentwise transport preserves the source, compact-subset, finite-window, Hausdorff, and Vietoris rows, while replay repeats the same displayed inspection path.

Thus the Vietoris scope is finite at every public read and contains no open-cover compactness coordinate, selected representative, quotient compactum, or host powerset.
\end{proof}

\closureat{CompactMetricHyperspaceUp}{seedStr}

\begin{closurestatus}{\CompactMetricHyperspaceUp}
  \constructivestory{A $\CompactMetricHyperspaceUp$ packet is generated from a CompactMetricUp source, a HyperspaceUp compact-subset ledger, finite nonempty subset windows, Hausdorff-distance readback, Vietoris finite-net scope, a Hausdorff-completion route, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-metric-hyperspace-carrier}, \autoref{thm:compact-metric-hyperspace-namecert-obligations}, \autoref{thm:compact-metric-hyperspace-hausdorff-completion-route}, and \autoref{thm:compact-metric-hyperspace-vietoris-finite-net-scope} seed the compact metric Hausdorff/Vietoris hyperspace surface over compact metric BEDC packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host powersets, quotient compacta, open-cover compactness, selected limits, choice-selected representatives, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite Hausdorff-window admission, Vietoris finite-net scope, Hausdorff-completion route stability, and provenance/name exhaustion for BEDC.Derived.CompactMetricHyperspaceUp.}
\end{closurestatus}
