\chapter{A Concrete Naming Certificate for $\RegularCauchyTailEquivalenceUp$}
\label{ch:concrete-instances-regular-cauchy-tail-equivalence-namecert}
\origin{human}

Following Bishop--Bridges constructive Cauchy real analysis, the $\RegularCauchyTailEquivalenceUp$ packet records the equality-facing tail classifier by which two regular rational Cauchy names reach the $\RealUp$ seal. It sits between the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the setoid comparison surface of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite L10 Real and Completion handoff; it is not quotient stream equality, a selected limit, countable choice, host real equality, or ambient completeness of $\RealUp$.

\begin{definition}[Regular Cauchy tail equivalence carrier]
\label{def:regular-cauchy-tail-equivalence-carrier}
A $\RegularCauchyTailEquivalenceUp$ carrier is a finite $\BHist$ packet
$$
E=(S_0,S_1,R_0,R_1,D,Q,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S_0$ and $S_1$ are the two $\StreamNameUp$ finite-window rows through which the source names are inspected.
\item $R_0$ and $R_1$ are the corresponding $\RegSeqRatUp$ readback rows exposed by those windows.
\item $D$ is the $\DyadicRatCoreUp$ tail-tolerance ledger, recording the requested precision, the two regular radii, the common-tail threshold, and the remaining comparison slack.
\item $Q$ is the $\CauchyEquivalenceSetoidUp$ comparison row tying the two readbacks to the finite reflexive, symmetric, and transitive classifier surface.
\item $A$ is the $\RealUp$ seal row reached only after the two windows, two readbacks, tolerance ledger, and setoid comparison have been displayed.
\item $H$ records componentwise $\hsame$ transport for windows, readbacks, tolerance ledger, setoid comparison, Real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from an equality-facing Real or Completion request through $S_0,S_1,R_0,R_1,D,Q,A,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyTailEquivalenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\CauchyEquivalenceSetoidUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyTailEquivalenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S_0,S_1,R_0,R_1,D,Q,A,H,C,P,N$. It has no coordinate for quotient classes, selected limits, countable choice, trichotomy, host real equality, or ambient real completeness.
\end{definition}

\begin{theorem}[Regular Cauchy tail equivalence NameCert obligations]
\label{thm:regular-cauchy-tail-equivalence-namecert-obligations}
For every accepted $\RegularCauchyTailEquivalenceUp$ carrier
$$
E=(S_0,S_1,R_0,R_1,D,Q,A,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyTailEquivalenceUp}$ surface consists exactly of two $\StreamNameUp$ window admissions, two $\RegSeqRatUp$ readbacks, one $\DyadicRatCoreUp$ tail-tolerance ledger, one $\CauchyEquivalenceSetoidUp$ comparison row, one $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-tail-equivalence-carrier}. The accepted tuple exposes exactly the two window rows, two regular readbacks, dyadic tolerance ledger, setoid comparison, Real seal, transport, replay, provenance, and naming rows.

The source side is exhausted by $S_0,S_1,R_0,R_1$. Every equality-facing request must inspect the finite windows and the corresponding regular rational readbacks before any tail comparison is available.

The comparison side is exhausted by $D$ and $Q$. The dyadic ledger stores the precision, radii, common-tail threshold, and slack, while the setoid row records the finite classifier comparison over the displayed readbacks.

The endpoint side is exhausted by $A,H,C,P,N$. These rows seal the comparison for $\RealUp$, transport it componentwise, replay the route, source it, and name it locally. Since the carrier contains no quotient, selected limit, choice, trichotomy, host equality, or completeness coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Regular Cauchy tail equivalence Real handoff]
\label{thm:regular-cauchy-tail-equivalence-real-handoff}
Every Real or Completion consumer of an accepted $\RegularCauchyTailEquivalenceUp$ packet must read the finite route
$$
S_0,S_1 \longmapsto R_0,R_1 \longmapsto D \longmapsto Q \longmapsto A
$$
before it may consume equality at the $\RealUp$ seal. Thus equality is exported only as a tail-tolerance classifier between displayed $\RegSeqRatUp$ readbacks, not as quotient stream equality or selected-limit equality.
\end{theorem}
\begin{proof}
Begin with a Real or Completion equality request. By \autoref{def:regular-cauchy-tail-equivalence-carrier}, the request first reaches the two finite window rows $S_0,S_1$ and their readbacks $R_0,R_1$.

The dyadic ledger $D$ is then the only tolerance source. It records the common-tail threshold and the remaining slack before the setoid comparison row $Q$ can be read.

Only downstream of $Q$ does the seal row $A$ become visible. The structural rows $H,C,P,N$ preserve this route and add no host equality coordinate.

Therefore a Real or Completion consumer receives the displayed finite classifier route and nothing stronger. Quotient stream equality, selected limits, countable choice, trichotomy, host real equality, and ambient completeness remain outside the packet.
\end{proof}

\falsifiablePrediction{Every accepted $\RegularCauchyTailEquivalenceUp$ read displays two $\StreamNameUp$ windows, two $\RegSeqRatUp$ readbacks, one $\DyadicRatCoreUp$ tail-tolerance ledger, one $\CauchyEquivalenceSetoidUp$ comparison row, one $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before Real or Completion equality is consumed.}

\independenceWitness{streamname, regseqrat, dyadicratcore, cauchy-equivalence-setoid, real: $\RegularCauchyTailEquivalenceUp$ is not bijective to any listed sibling because it binds two window rows, two regular readbacks, one tail-tolerance ledger, one setoid comparison row, one Real seal, componentwise transport, replay, provenance, and local naming into a single L10 equality-facing carrier.}

\closureat{RegularCauchyTailEquivalenceUp}{seedStr}

\begin{closurestatus}{\RegularCauchyTailEquivalenceUp}
  \constructivestory{A $\RegularCauchyTailEquivalenceUp$ packet is generated from two StreamName windows, two RegSeqRat readbacks, one DyadicRatCore tail-tolerance ledger, one CauchyEquivalenceSetoid comparison row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-tail-equivalence-carrier}, \autoref{thm:regular-cauchy-tail-equivalence-namecert-obligations}, and \autoref{thm:regular-cauchy-tail-equivalence-real-handoff} seed the finite L10 Real and Completion tail-equivalence classifier between RegSeqRat readbacks and Real equality.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, trichotomy, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked window admission, regular readback, dyadic tolerance accounting, setoid comparison, Real seal handoff, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyTailEquivalenceUp.}
\end{closurestatus}
