\chapter{A Concrete Naming Certificate for $\LocatedCauchyBracketUp$}
\label{ch:concrete-instances-located-cauchy-bracket-namecert}
\origin{human}

Following Bishop and Bridges, Constructive Analysis, 1985, the $\LocatedCauchyBracketUp$ packet records explicit finite bracket data for a regular Cauchy rational name before the L10 Real and Completion route reads the terminal real seal. It sits over the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, the endpoint interval surface of \autoref{ch:concrete-instances-locatedinterval-namecert}, and the located real boundary of \autoref{ch:concrete-instances-locatedreal-namecert}. The packet names only inspected brackets, tolerance rows, transport, replay, provenance, and local naming; it is not a quotient-real equality, selected limit, trichotomy, countable-choice schedule, or ambient completeness principle.

\begin{definition}[Located Cauchy bracket carrier]
\label{def:located-cauchy-bracket-carrier}
A $\LocatedCauchyBracketUp$ carrier is a finite $\BHist$ packet
$$
B=(L,U,D,W,R,I,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ and $U$ are lower and upper $\DyadicRatCoreUp$ endpoint rows for the inspected bracket.
\item $D$ is the dyadic radius row certifying the requested bracket width.
\item $W$ is the finite $\StreamNameUp$ observation window from which the source Cauchy data are read.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from $W$ under the displayed radius ledger.
\item $I$ is the $\LocatedIntervalUp$ row whose endpoints are $L$ and $U$ and whose containment ledger covers the readback window.
\item $E$ is the terminal $\RealUp$ and $\LocatedRealUp$ seal row reached through the displayed bracket.
\item $H$ records componentwise $\hsame$ transport for $L,U,D,W,R,I,E$ and the local naming row.
\item $C$ records displayed $\Cont$ replay from a bracket request through dyadic endpoints, stream observations, regular readback, located interval containment, and the real seal.
\item $P$ is the $\Pkg$ provenance over $\LocatedCauchyBracketUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\LocatedIntervalUp$, $\LocatedRealUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedCauchyBracketUp}$ row.
\end{enumerate}
The classifier compares accepted bracket packets only through $L,U,D,W,R,I,E,H,C,P,N$. It has no coordinate for a quotient stream, selected host limit, host real equality, trichotomy oracle, countable choice, or ambient $\RealUp$ completeness witness.
\end{definition}

\begin{theorem}[Located Cauchy bracket shrink]
\label{thm:located-cauchy-bracket-shrink}
For every accepted $\LocatedCauchyBracketUp$ carrier $B=(L,U,D,W,R,I,E,H,C,P,N)$ and every displayed successor precision request carried by the same $\StreamNameUp$ schedule, the bracket can be read through a successor dyadic radius row $D'$ and a refined located interval row $I'$ while preserving the original $\RegSeqRatUp$ readback route, terminal $\RealUp$ seal route, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The shrink exports no quotient stream, selected limit, host real equality, trichotomy, countable-choice selector, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the carrier rows. The only analytic data available to a successor precision read are the displayed endpoints $L,U$, the radius row $D$, the finite window $W$, the readback $R$, and the located interval row $I$.

Use the dyadic tolerance refinement from \autoref{ch:concrete-instances-dyadicratcore-namecert} and keep the observation on the same $\StreamNameUp$ schedule. The refined radius $D'$ and interval row $I'$ are therefore componentwise refinements of displayed rows, not new host data.

Finally replay the $\RegSeqRatUp$ and $\RealUp$ handoff through $H,C,P,N$. Since the carrier has no coordinate for a quotient stream, selected limit, host equality, trichotomy, choice, or ambient completeness, the refined bracket preserves the same finite seal route and exports nothing outside it.
\end{proof}

\begin{theorem}[Located Cauchy bracket Real seal]
\label{thm:located-cauchy-bracket-real-seal}
Every $\RealUp$, $\LocatedRealUp$, or Completion-facing consumer of an accepted $\LocatedCauchyBracketUp$ packet reaches the terminal real seal only through the displayed finite route
$$
\DyadicRatCoreUp
\longmapsto
\StreamNameUp
\longmapsto
\RegSeqRatUp
\longmapsto
\LocatedIntervalUp
\longmapsto
\LocatedRealUp
\longmapsto
\RealUp .
$$
The route may consume dyadic bracket endpoints, a dyadic radius row, finite stream observations, regular rational readback, located interval containment, componentwise transport, replay, provenance, and local naming, but it cannot replace them by a quotient-real representative, selected limit, host interval primitive, trichotomy oracle, countable choice, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with the displayed carrier of \autoref{def:located-cauchy-bracket-carrier}. The endpoint and radius rows expose the dyadic bracket before any stream or real-seal read is available.

The finite window $W$ and readback $R$ then supply the regular Cauchy observation surface. The located interval row $I$ binds that readback between the displayed dyadic endpoints, so a Real-facing consumer cannot bypass the bracket by selecting a host representative.

The terminal seal row $E$ is downstream of $I$ and is replayed only through $H,C,P,N$. Thus the stated route exhausts the visible rows and excludes quotient representatives, selected limits, host interval primitives, trichotomy, choice, and ambient completeness.
\end{proof}

\closureat{LocatedCauchyBracketUp}{seedStr}

\begin{closurestatus}{\LocatedCauchyBracketUp}
  \constructivestory{A $\LocatedCauchyBracketUp$ packet is generated from dyadic lower and upper endpoints, a dyadic radius row, a finite StreamNameUp observation window, RegSeqRatUp readback, a LocatedIntervalUp containment row, a LocatedRealUp and RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-cauchy-bracket-carrier}, \autoref{thm:located-cauchy-bracket-shrink}, and \autoref{thm:located-cauchy-bracket-real-seal} seed the finite located Cauchy bracket route for L10 Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient real equality, selected limits, host real equality, trichotomy, countable choice, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, bracket shrink, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.LocatedCauchyBracketUp.}
\end{closurestatus}
