\chapter{A Concrete Naming Certificate for $\HigsonCompactificationUp$}
\label{ch:concrete-instances-higson-compactification-namecert}
\origin{human}

Following Higson and Roe on coarse topology, the $\HigsonCompactificationUp$ packet records the compactification read by slowly oscillating bounded continuous functions on a large-scale metric or uniform source. It sits after the uniform-space carrier of \autoref{ch:concrete-instances-uniformspace-namecert}, the metric observation surface of \autoref{ch:concrete-instances-metric-namecert}, the compact target boundary of \autoref{ch:concrete-instances-compact-namecert}, the continuous-map row of \autoref{ch:concrete-instances-continuousmap-namecert}, and the terminal real-valued readback of \autoref{ch:concrete-instances-real-namecert}. It is adjacent to the uniform-envelope route of \autoref{ch:concrete-instances-samuel-compactification-namecert} and the bounded-function envelope of \autoref{ch:concrete-instances-stone-cech-compactification-namecert}, but its local carrier keeps the coarse-control row visible rather than collapsing to either sibling.

\begin{definition}[Higson compactification carrier]
\label{def:higson-compactification-carrier}
A $\HigsonCompactificationUp$ carrier is a finite $\BHist$ packet
$$
K=(U,M,A,C,F,R,S,B,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\UniformSpaceUp$ source row supplying entourages and uniform refinement data for the underlying space;
\item $M$ is the $\MetricUp$ large-scale control row recording bounded-set, coarse-separation, and distance-window requests;
\item $A$ is the Higson-algebra row of bounded real-valued functions whose oscillation is eventually small outside controlled bounded regions;
\item $C$ is the $\ContinuousMapUp$ row proving that every accepted function in $A$ is read through displayed continuity data;
\item $F$ is the finite observation-family row used by a consumer to inspect only finitely many Higson functions at a requested stage;
\item $R$ is the $\RealUp$ value-seal row for the bounded real observations in $A$ and $F$;
\item $S$ is the Samuel-compactification comparison row imported from \autoref{ch:concrete-instances-samuel-compactification-namecert};
\item $B$ is the Stone--Cech comparison row imported from \autoref{ch:concrete-instances-stone-cech-compactification-namecert};
\item $H$ records componentwise $\hsame$ transport for $U,M,A,C,F,R,S,B,T,P,N$;
\item $T$ records displayed $\Cont$ replay of coarse-control and function-evaluation requests;
\item $P$ is the $\Pkg$ provenance over $\UniformSpaceUp$, $\MetricUp$, $\CompactUp$, $\ContinuousMapUp$, $\RealUp$, the two compactification neighbours, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\HigsonCompactificationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. There is no coordinate for a selected boundary point, ultrafilter choice, quotient host compactification, full Stone--Cech universality, or ambient properness theorem.
\end{definition}

\begin{theorem}[Higson compactification NameCert obligations]
\label{thm:higson-compactification-namecert-obligations}
For every accepted $\HigsonCompactificationUp$ carrier
$$
K=(U,M,A,C,F,R,S,B,H,T,P,N),
$$
the local $\NameCert_{\HigsonCompactificationUp}$ surface consists exactly of carrier admission for the uniform source, large-scale metric row, slowly oscillating bounded function row, continuity row, finite observation family, real value seals, Samuel comparison, Stone--Cech comparison, componentwise transport, replay, provenance, and local naming.

The obligation surface also records coarse-control non-escape: every accepted real-valued observation must pass through $M,A,C,F,R$ before it is read as compactification data, and the comparison rows $S,B$ do not replace the Higson algebra row by Samuel uniformity alone or by Stone--Cech bounded functions alone.
\end{theorem}
\begin{proof}
Project the carrier $K$. The rows $U$ and $M$ expose the uniform and large-scale source data, while $A,C,F,R$ expose the slowly oscillating bounded functions, their continuity witnesses, finite observation families, and real value seals.

The comparison rows are then read as neighbours rather than definitions. Row $S$ identifies the Samuel compactification route available from uniform data, and row $B$ identifies the Stone--Cech bounded-function envelope, but neither row carries the coarse-control predicate stored in $A$ over the metric row $M$.

The structural rows $H,T,P,N$ transport, replay, package, and name exactly the displayed route. Since the carrier has no further coordinate, a consumer cannot obtain a selected boundary point, an ultrafilter, a quotient host compactification, full Stone--Cech universality, or an ambient properness theorem from the local NameCert surface.
\end{proof}

\begin{theorem}[Higson compactification uniform handoff]
\label{thm:higson-compactification-uniform-handoff}
Every compactification-facing consumer of an accepted $\HigsonCompactificationUp$ packet factors through the route
$$
U,M \longmapsto A,C,F,R \longmapsto S,B,H,T,P,N .
$$
Thus the consumer first reads the uniform and large-scale metric source rows, then the slowly oscillating bounded continuous real-valued observation rows, and only then the Samuel and Stone--Cech comparison rows together with transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(U,M,A,C,F,R,S,B,H,T,P,N)$. The only source rows are $U$ and $M$, so every compactification-facing request begins with the displayed uniform and large-scale metric data.

The Higson observation rows are downstream of that source. Row $A$ records the slowly oscillating bounded real-valued functions, $C$ keeps their continuity evidence visible, $F$ restricts consumer inspection to finite observation families, and $R$ seals the observed values as $\RealUp$ data.

The neighbour rows $S$ and $B$ are consumed after the Higson observation route has been read. They compare the packet with Samuel and Stone--Cech compactification surfaces, while $H,T,P,N$ retain transport, replay, provenance, and local naming for the same displayed rows. No bypass row exists for selected boundary points, ultrafilters, quotient host compactifications, full Stone--Cech universality, or ambient properness.
\end{proof}

\falsifiablePrediction{Every $\HigsonCompactificationUp$ compactification-facing read exposes a $\UniformSpaceUp$ row, a $\MetricUp$ large-scale row, a slowly oscillating bounded $\ContinuousMapUp$ row, finite observation data, $\RealUp$ value seals, Samuel and Stone--Cech comparison rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{uniformspace, metric, compact, continuousmap, real, samuel-compactification, stone-cech-compactification: $\HigsonCompactificationUp$ is not bijective to any listed sibling because it binds coarse-control and slowly oscillating bounded continuous real-valued observations together with the two compactification comparison rows in one finite carrier.}

\closureat{HigsonCompactificationUp}{seedStr}

\begin{closurestatus}{\HigsonCompactificationUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:higson-compactification-carrier}, \autoref{thm:higson-compactification-namecert-obligations}, and \autoref{thm:higson-compactification-uniform-handoff} seed the finite Higson compactification packet through uniform, metric, compact, continuous-map, Real, Samuel, and Stone--Cech rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected boundary points, ultrafilter choice, quotient host compactifications, full Stone--Cech universality, ambient properness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, coarse-control exactness, slowly oscillating bounded function stability, finite observation replay, neighbour comparison non-collapse, provenance, and local naming.}
  \constructivestory{A $\HigsonCompactificationUp$ packet is generated from displayed uniform and large-scale metric source rows, slowly oscillating bounded continuous real-valued observations, finite observation families, Samuel and Stone--Cech comparison rows, componentwise transport, replay, provenance, and a local $\NameCert$ row.}
\end{closurestatus}
