\chapter{A Concrete Naming Certificate for $\ObserverLocalityRateBudgetUp$}
\label{ch:concrete-instances-observer-locality-rate-budget-namecert}
\origin{ai}

The $\ObserverLocalityRateBudgetUp$ packet realizes the Inter-Hist Locality maximum-rate read as a finite paired-observer budget rather than as a global frame, metric tensor, or host-valued speed. It consumes the multi-history configuration route of \autoref{ch:concrete-instances-multihistconfig-namecert}, the cross-Hist causal route of \autoref{ch:concrete-instances-crosshistcausal-namecert}, the maximum causal-rate surface of \autoref{ch:concrete-instances-maxcausalrate-namecert}, the public maximum-rate gate of \autoref{ch:concrete-instances-maxratereadgate-namecert}, and the rate-boundary refusal of \autoref{ch:concrete-instances-inter-hist-rate-boundary-namecert}. The packet is a concrete finite budget for observer-locality reads; it is not a global synchronization row, privileged frame, hidden clock, ambient metric geometry, or selected real-valued velocity.

\begin{definition}[Observer locality rate-budget carrier]
\label{def:observer-locality-rate-budget-carrier}
An $\ObserverLocalityRateBudgetUp$ carrier is a finite $\BHist$ packet
$$
B=(M,C,R,G,S,T,N,H,K,P)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the paired $\mathsf{MultiHistConfig}$ row, naming the two observer histories and their local history classifiers without adding a global synchronization row.
\item $C$ is the $\mathsf{CrossHistCausal}$ row, recording the displayed causal-dependence reads between the two histories.
\item $R$ is the $\mathsf{MaxCausalRate}$ row, exposing the maximum-rate bound only as a finite causal-rate read over $M$ and $C$.
\item $G$ is the $\mathsf{MaxRateReadGate}$ row, requiring observer-symmetry and no-global-frame refusal before the rate read becomes public.
\item $S$ is the observer-symmetry budget row, recording the two-direction comparison that prevents either history from serving as the privileged frame.
\item $T$ is the transport row for paired-history $\hsame$ and $\psame$ movement across the same causal-rate budget.
\item $N$ is the no-global-frame refusal row, blocking shared clocks, global coordinates, metric tensors, host speeds, and selected synchronization data.
\item $H$ records componentwise $\hsame$ transport for the paired histories, causal row, rate row, read gate, symmetry budget, transport, refusal, replay, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay from a requested public rate read through $M,C,R,G,S,T,N$ and then to the structural rows.
\item $P$ is the $\Pkg$ provenance and local $\NameCert_{\ObserverLocalityRateBudgetUp}$ naming row over the displayed packet.
\end{enumerate}
The classifier compares accepted packets only through $M,C,R,G,S,T,N,H,K,P$. It has no coordinate for a global frame, universal clock, metric geometry, host real-valued speed, selected observer representative, or choice principle.
\end{definition}

\begin{theorem}[Observer locality rate-budget NameCert obligations]
\label{thm:observer-locality-rate-budget-namecert-obligations}
For every accepted $\ObserverLocalityRateBudgetUp$ carrier $B=(M,C,R,G,S,T,N,H,K,P)$, the local $\NameCert_{\ObserverLocalityRateBudgetUp}$ surface consists exactly of the following obligation rows:
\begin{enumerate}
\item paired-history admission through $M$;
\item cross-Hist causal admission through $C$;
\item maximum causal-rate admission through $R$;
\item public maximum-rate gating through $G$;
\item observer-symmetry budgeting through $S$;
\item paired-history transport through $T,H$;
\item no-global-frame refusal through $N$;
\item displayed replay, provenance, and local naming through $K,P$.
\end{enumerate}
Every public maximum-rate read must pass through the observer-symmetry budget and the no-global-frame refusal before a consumer may cite the rate bound.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:observer-locality-rate-budget-carrier}. The paired histories enter through $M$, causal dependence through $C$, and the maximum-rate bound through $R$.

The read cannot become public at that point. The gate row $G$ requires the observer-symmetry budget $S$ and the no-global-frame refusal row $N$, while $T$ and $H$ preserve the paired-history route under displayed transport.

Finally replay and provenance are supplied by $K,P$. Because the carrier contains no further rows, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Observer locality rate-budget nonescape]
\label{thm:observer-locality-rate-budget-nonescape}
Every public rate read exported by an accepted $\ObserverLocalityRateBudgetUp$ carrier factors through
$$
M,C,R,G,S,T,N,H,K,P .
$$
In particular, omitting either the observer-symmetry budget $S$ or the no-global-frame refusal $N$ prevents the read from being public. The packet exports no global frame, universal clock, ambient metric geometry, selected observer representative, host real-valued velocity, or choice principle.
\end{theorem}
\begin{proof}
Begin with a public rate read. By \autoref{thm:observer-locality-rate-budget-namecert-obligations}, the read must expose paired histories, cross-Hist causality, and maximum causal-rate data through $M,C,R$.

The gate row $G$ then checks the symmetry budget $S$ and no-global-frame refusal $N$. If either row is absent, the requested read lacks one of the named obligations and cannot pass the local certificate.

Transport and replay through $T,H,K$ preserve that same route, and $P$ names it. Since the excluded global-frame, clock, metric, selected-observer, host-velocity, and choice data are absent from the carrier, they cannot be exported.
\end{proof}

\begin{theorem}[Observer locality rate-budget Lean carrier boundary]
\label{thm:observer-locality-rate-budget-lean-carrier-boundary}
The follow-up Lean carrier for $\ObserverLocalityRateBudgetUp$ must expose a nontrivial public object and a field-faithful public classifier in `lean4/BEDC/Derived/ObserverLocalityRateBudgetUp/TasteGate.lean`. Concretely, the carrier boundary is satisfied only when the Lean side provides `Nontrivial ObserverLocalityRateBudgetUp` and `FieldFaithful ObserverLocalityRateBudgetUp` for the same finite rows displayed in \autoref{def:observer-locality-rate-budget-carrier}.
\end{theorem}
\begin{proof}
The paper-side packet is not a purely verbal refusal; it carries the finite rows $M,C,R,G,S,T,N,H,K,P$. A Lean carrier that collapsed those rows to a singleton without public field separation would fail to represent the observer-symmetry and no-global-frame budget as distinguishable data.

The required nontriviality gives at least one public object boundary beyond the empty carrier. Field faithfulness then ties the public classifier to the displayed rows, so a maximum-rate read cannot be accepted after erasing the symmetry or refusal coordinates.

Thus the Lean follow-up must provide both named interfaces in the indicated TasteGate file before the carrier can be treated as a faithful formal companion to this chapter.
\end{proof}

\falsifiablePrediction{Any public $\ObserverLocalityRateBudgetUp$ maximum-rate read that omits either observer-symmetry or no-global-frame refusal refutes the packet.}

\independenceWitness{multihistconfig, crosshistcausal, maxcausalrate, maxratereadgate, interhistrateboundary: $\ObserverLocalityRateBudgetUp$ is not bijective to any listed sibling because it jointly carries paired histories, causal rows, maximum-rate rows, public read gating, observer-symmetry budgets, no-global-frame refusal, transport, replay, provenance, and local naming.}

\closureat{ObserverLocalityRateBudgetUp}{seedStr}

\begin{closurestatus}{\ObserverLocalityRateBudgetUp}
  \constructivestory{An $\ObserverLocalityRateBudgetUp$ packet is generated from paired MultiHistConfig rows, CrossHistCausal rows, MaxCausalRate rows, MaxRateReadGate rows, observer-symmetry budgets, transport rows, no-global-frame refusal, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:observer-locality-rate-budget-carrier}, \autoref{thm:observer-locality-rate-budget-namecert-obligations}, \autoref{thm:observer-locality-rate-budget-nonescape}, and \autoref{thm:observer-locality-rate-budget-lean-carrier-boundary} seed the finite observer-locality rate-budget certificate surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global synchronization, privileged frames, hidden clocks, ambient metric geometry, selected observers, host real-valued velocities, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked paired-history admission, causal-row admission, maximum-rate admission, read-gate exactness, observer-symmetry budgeting, no-global-frame refusal, transport, replay, provenance, local naming, nontriviality, and field faithfulness for BEDC.Derived.ObserverLocalityRateBudgetUp.}
\end{closurestatus}
