\chapter{A Concrete Naming Certificate for $\FiniteCoverRadiusStabilityUp$}
\label{ch:concrete-instances-finite-cover-radius-stability-namecert}
\origin{human}

Following Bishop--Bridges finite-cover compactness practice, the $\FiniteCoverRadiusStabilityUp$ packet records the finite radius-stability object consumed by the compact-uniform-continuity fold of \autoref{ch:visions-compact-uniform-continuity}. It sits between the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-map pointwise modulus rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the positive rational-radius rows of \autoref{ch:concrete-instances-rat-namecert}, the lower-bound fold of \autoref{ch:concrete-instances-finitenetminimumfold-namecert}, and the downstream $\UniformModulusUp$ consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet makes the finite cover radius ledger explicit, not a choice of Lebesgue number from an open-cover theorem, not a host compactness principle, and not an external modulus selector.

\begin{definition}[FiniteCoverRadiusStability carrier]
\label{def:finite-cover-radius-stability-carrier}
A $\FiniteCoverRadiusStabilityUp$ carrier is a finite $\BHist$ packet
$$
F=(K,M,\mathcal{P},R,L,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row carrying the finite net and located-distance coverage data.
\item $M$ is the $\ContinuousMapUp$ pointwise-modulus row read at the bundled centers.
\item $\mathcal{P}$ is the nonempty $\mathsf{ProbeBundle}$ cover spine for the selected finite net.
\item $R$ is the finite family of positive $\RatUp$ radius rows, one for each bundled probe.
\item $L$ is the $\FiniteNetMinimumFoldUp$ lower-bound fold row certifying a positive radius below every displayed row in $R$.
\item $U$ is the $\UniformModulusUp$ handoff row receiving the folded radius as a tolerance-only precision ledger.
\item $H$ records componentwise $\hsame$ transport for the compact source, continuous-map row, bundle spine, radius family, fold row, uniform-modulus handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from compact finite-net coverage through pointwise radii, lower-bound folding, and uniform-modulus handoff.
\item $P$ is the $\Pkg$ provenance over $\FiniteCoverRadiusStabilityUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\RatUp$, $\FiniteNetMinimumFoldUp$, $\UniformModulusUp$, $\mathsf{ProbeBundle}$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FiniteCoverRadiusStabilityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an open-cover compactness theorem, an external Lebesgue-number selector, a chosen center outside $\mathcal{P}$, quotient point equality, countable choice, or ambient real completeness.
\end{definition}

\begin{theorem}[FiniteCoverRadiusStability NameCert obligations]
\label{thm:finite-cover-radius-stability-obligations}
For every accepted $\FiniteCoverRadiusStabilityUp$ carrier
$$
F=(K,M,\mathcal{P},R,L,U,H,C,P,N),
$$
the local $\NameCert_{\FiniteCoverRadiusStabilityUp}$ surface consists exactly of compact metric source exposure, continuous pointwise-modulus exposure, finite $\mathsf{ProbeBundle}$ cover admission, positive $\RatUp$ radius admission, lower-bound fold exactness, $\UniformModulusUp$ handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every uniform-modulus consumer must expose $K,M,\mathcal{P},R,L$ before $U$ can be read.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-cover-radius-stability-carrier}. The compact source, pointwise modulus, finite bundle, radius family, lower-bound fold, and uniform-modulus handoff are exactly the analytic rows.

The compact metric row $K$ supplies only displayed finite-net coverage. The continuous-map row $M$ supplies the pointwise-radius data attached to the centers named by the bundle spine $\mathcal{P}$.

The radius family $R$ is folded by $L$ inside the same finite bundle. Thus the downstream row $U$ receives a classifier-stable positive lower bound rather than a host-selected Lebesgue number.

Rows $H,C,P,N$ transport, replay, source, and name the same displayed route. Since no excluded open-cover, choice, quotient, or external-selector coordinate is present, these obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[FiniteCoverRadiusStability uniform-modulus handoff]
\label{thm:finite-cover-radius-stability-uniform-modulus-handoff}
Every compact-uniform-continuity consumer accepted by a $\FiniteCoverRadiusStabilityUp$ carrier receives its $\UniformModulusUp$ precision row only through the finite route
$$
\CompactMetricUp \longmapsto \ContinuousMapUp \longmapsto \RatUp \longmapsto \FiniteNetMinimumFoldUp \longmapsto \UniformModulusUp
$$
over the displayed $\mathsf{ProbeBundle}$ spine. The handoff preserves the compact finite-net coverage, pointwise radius rows, positive rational lower-bound fold, componentwise transport, replay, provenance, and local naming rows, and it exports no open-cover compactness theorem, external Lebesgue-number selector, chosen center outside the bundle, quotient point equality, countable choice, or ambient completeness principle.
\end{theorem}
\begin{proof}
Start with an accepted carrier $F=(K,M,\mathcal{P},R,L,U,H,C,P,N)$. The finite-net cover is read from $K$ and indexed by the displayed bundle $\mathcal{P}$.

At each bundled center, the continuous-map row $M$ supplies a pointwise modulus radius. The row $R$ stores those positive $\RatUp$ radius histories as the finite family to be folded.

Apply the lower-bound row $L$. It certifies one radius below every displayed member of $R$, so the handoff row $U$ receives a tolerance-only precision ledger produced inside the same finite route.

Transport, replay, provenance, and naming are carried by $H,C,P,N$. Because the carrier has no open-cover, external-selector, quotient, choice, or ambient-completeness coordinate, every uniform-modulus consumer remains confined to the displayed radius-stability packet.
\end{proof}

\closureat{FiniteCoverRadiusStabilityUp}{seedStr}

\begin{closurestatus}{\FiniteCoverRadiusStabilityUp}
  \constructivestory{A $\FiniteCoverRadiusStabilityUp$ packet is generated from a CompactMetric source row, ContinuousMap pointwise-modulus row, ProbeBundle finite cover spine, positive RatUp radius rows, FiniteNetMinimumFold lower-bound row, UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-cover-radius-stability-carrier}, \autoref{thm:finite-cover-radius-stability-obligations}, and \autoref{thm:finite-cover-radius-stability-uniform-modulus-handoff} seed the finite radius-stability surface used by compact-uniform-continuity consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, external Lebesgue-number selection, centers outside the displayed bundle, quotient point equality, countable choice, ambient real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net exposure, continuous pointwise-radius exposure, positive RatUp radius admission, finite lower-bound fold exactness, UniformModulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.FiniteCoverRadiusStabilityUp.}
\end{closurestatus}
