\chapter{A Concrete Naming Certificate for $\UniformLebesgueNumberUp$}
\label{ch:concrete-instances-uniform-lebesgue-number-namecert}
\origin{human}

Following Lebesgue's covering lemma, Bourbaki and Kelley on uniform spaces, and Bishop--Bridges compact metric analysis, the $\UniformLebesgueNumberUp$ packet records the radius handoff by which a compact-cover lower bound becomes uniform entourage data. It sits after the compact finite-radius packet of \autoref{ch:concrete-instances-compact-lebesgue-number-namecert}, the finite lower-radius fold of \autoref{ch:concrete-instances-finite-lebesgue-number-namecert}, the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, and the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet is a finite NameCert boundary for uniform reads of compact cover radii; it is not an arbitrary open-cover principle, not a selected subcover, and not an ambient minimum theorem.

\begin{definition}[Uniform Lebesgue-number carrier]
\label{def:uniform-lebesgue-number-carrier}
A $\UniformLebesgueNumberUp$ carrier is a finite $\BHist$ packet
$$
U=(K,M,F,V,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row whose compact finite-net and cover-inspection data must be read before any radius is exported.
\item $M$ is the $\MetricUp$ distance row that interprets every cover-radius and entourage request as metric evidence.
\item $F$ is the $\FiniteLebesgueNumberUp$ lower-bound fold row for the finite cover-radius ledger.
\item $V$ is the $\UniformModulusUp$ consumer row that receives the lower-bound ledger as a tolerance-only uniform handoff.
\item $L$ is the $\CompactLebesgueNumberUp$ route row, carrying the compact cover spine, located coverage rows, positive radius ledger, and finite lower-bound fold together.
\item $H$ records componentwise $\hsame$ transport for the compact source, metric row, finite lower-bound fold, uniform-modulus handoff, compact Lebesgue-number route, replay, provenance, and local name.
\item $C$ records displayed $\Cont$ replay of the route
$$
K,M,L \longmapsto F \longmapsto V .
$$
\item $P$ is the $\Pkg$ provenance over $\UniformLebesgueNumberUp$, $\CompactMetricUp$, $\MetricUp$, $\FiniteLebesgueNumberUp$, $\UniformModulusUp$, $\CompactLebesgueNumberUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\UniformLebesgueNumberUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,M,F,V,L,H,C,P,N$. It has no coordinate for arbitrary open covers, selected subcovers, host compactness, host minima, quotient real equality, countable choice, or a uniform radius detached from the compact finite cover ledger.
\end{definition}

\begin{theorem}[Uniform Lebesgue-number NameCert obligations]
\label{thm:uniform-lebesgue-number-namecert-obligations}
For every accepted $\UniformLebesgueNumberUp$ carrier
$$
U=(K,M,F,V,L,H,C,P,N),
$$
the local $\NameCert_{\UniformLebesgueNumberUp}$ surface consists exactly of the following finite rows:
\begin{enumerate}
\item carrier admission for the nine displayed rows;
\item compact-metric source exposure, requiring every uniform-radius read to pass through $K$;
\item metric interpretation, requiring $M$ to mediate every radius and entourage request before it reaches a uniform consumer;
\item finite Lebesgue-number compatibility, requiring $F$ to be the lower-bound fold of the displayed compact cover-radius ledger;
\item compact Lebesgue-number route compatibility, requiring $L$ to expose the compact cover spine, located coverage rows, positive radius ledger, and finite lower-bound fold before $V$ is available;
\item uniform-modulus handoff, requiring $V$ to consume only the displayed lower-bound ledger routed through $K,M,F,L$;
\item componentwise transport, displayed replay, provenance, and local naming for the same route through $H,C,P,N$.
\end{enumerate}
No uniform Lebesgue-number obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $U=(K,M,F,V,L,H,C,P,N)$. The displayed coordinates give the compact source, metric interpretation, finite lower-bound fold, uniform-modulus handoff, compact Lebesgue-number route, and structural rows.

The compact and metric rows come first. The row $K$ supplies compact finite-net and cover-inspection data, while $M$ keeps radius and entourage reads inside the displayed metric surface.

The finite lower-bound row is then read through $F$ and $L$. The row $L$ carries the compact cover spine, located coverage rows, positive radius ledger, and finite lower-bound fold, so $F$ is not a host minimum and not a selected subcover argument.

Finally $V,H,C,P,N$ package the same lower-bound ledger for uniform-modulus consumers. Since the excluded objects do not occur as carrier coordinates, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Uniform Lebesgue-number compact-uniform handoff]
\label{thm:uniform-lebesgue-number-compact-uniform-handoff}
Every compact-uniform-continuity consumer of an accepted $\UniformLebesgueNumberUp$ carrier receives the finite route
$$
\CompactMetricUp,\MetricUp,\CompactLebesgueNumberUp
\longmapsto
\FiniteLebesgueNumberUp
\longmapsto
\UniformModulusUp
\longmapsto
\hsame,\Cont,\Pkg,\NameCert .
$$
Thus the compact cover-radius handoff of \autoref{ch:visions-compact-uniform-continuity} is exposed as compact-metric source data, metric radius interpretation, compact Lebesgue-number cover rows, a finite lower-bound fold, and a uniform-modulus consumer row. It exports no arbitrary open cover, selected subcover, host compactness theorem, host minimum, countable-choice selector, quotient real equality, or detached uniform radius.
\end{theorem}
\begin{proof}
Start from the source rows $K$ and $M$. They force every radius read to use the compact-metric source and the displayed metric interpretation before a uniform consumer can inspect the packet.

Read the compact Lebesgue-number route $L$. By \autoref{thm:compact-lebesgue-number-uniform-modulus-handoff}, that route exposes the compact cover spine, located coverage rows, positive radius ledger, and finite lower-bound fold before the uniform handoff is available.

The row $F$ records the finite $\FiniteLebesgueNumberUp$ lower-bound fold, and $V$ consumes exactly that lower-bound ledger as a $\UniformModulusUp$ row. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite path.

Because the carrier has no coordinate for arbitrary open covers, selected subcovers, host minima, choice, quotient real equality, or detached uniform radii, every compact-uniform read factors through the displayed route.
\end{proof}

\falsifiablePrediction{An accepted $\UniformLebesgueNumberUp$ read is refuted if a compact-uniform-continuity consumer exports a UniformModulusUp row without displaying CompactMetric source data, Metric radius interpretation, a CompactLebesgueNumber cover route, a FiniteLebesgueNumber lower-bound fold, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{compact-lebesgue-number, finite-lebesgue-number, uniformmodulus: none alone is bijective with $\UniformLebesgueNumberUp$ because the packet jointly carries compact source data, metric radius interpretation, compact cover rows, finite lower-bound fold, uniform-modulus handoff, transport, replay, provenance, and local NameCert.}

\closureat{UniformLebesgueNumberUp}{seedStr}

\begin{closurestatus}{\UniformLebesgueNumberUp}
  \constructivestory{A $\UniformLebesgueNumberUp$ packet is generated from CompactMetricUp source data, MetricUp radius interpretation, a CompactLebesgueNumberUp route row, a FiniteLebesgueNumberUp lower-bound fold, UniformModulusUp handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-lebesgue-number-carrier}, \autoref{thm:uniform-lebesgue-number-namecert-obligations}, and \autoref{thm:uniform-lebesgue-number-compact-uniform-handoff} seed the uniform Lebesgue-number packet from compact finite cover-radius data through lower-bound folds to UniformModulusUp handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close arbitrary open-cover compactness, selected subcovers, host compactness, host minima, quotient real equality, countable choice, detached uniform radii, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked compact-source exposure, metric radius interpretation, CompactLebesgueNumber route compatibility, FiniteLebesgueNumber fold compatibility, UniformModulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.UniformLebesgueNumberUp.}
\end{closurestatus}
