\chapter{A Concrete Naming Certificate for $\CompactUniformHomeomorphismUp$}
\label{ch:concrete-instances-compact-uniform-homeomorphism-namecert}
\origin{human}

Following the compact-metric uniform-continuity theorem as presented in Munkres and in Bishop--Bridges, the $\CompactUniformHomeomorphismUp$ packet records the finite certificate surface that turns a displayed compact metric homeomorphism into an inverse-uniform-continuity route. It consumes the finite cover and total-boundedness rows of \autoref{ch:concrete-instances-compactmetric-namecert} and \autoref{ch:concrete-instances-totallybounded-namecert}, the function and continuity rows of \autoref{ch:concrete-instances-continuousmap-namecert}, the distance interface of \autoref{ch:concrete-instances-metric-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The inverse modulus is read from finite-net and separated-target rows; it is not read from choice, open-cover compactness, host equality, or ambient Real completeness.

\begin{definition}[CompactUniformHomeomorphism carrier]\label{def:compact-uniform-homeomorphism-carrier}
A $\CompactUniformHomeomorphismUp$ carrier is a finite $\BHist$ packet
$$
U=(X,Y,M,T,F,G,A,B,E,S,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X,Y$ are the source and target $\MetricSpaceUp$ carrier rows.
\item $M$ is the $\CompactMetricUp$ finite-cover row for the source metric space.
\item $T$ is the $\TotallyBoundedUp$ finite-net row read from $M$ at each displayed dyadic scale.
\item $F$ is the forward $\ContinuousMapUp$ row and $G$ is the displayed inverse map row on the same named carrier windows.
\item $A$ records the finite graph-window agreement that $G(F(x))$ and $F(G(y))$ return to the displayed source and target windows through componentwise classifier reads.
\item $B$ is the separated-target ledger: for every finite net row and positive target separation request it displays the finite list of source cells whose forward images are classifier-separated in $Y$.
\item $E$ is the inverse-modulus row obtained by refining $T$ until the separated-target ledger $B$ accepts the target tolerance.
\item $S$ is the $\StreamNameUp$ finite-window row opened for source and target observations.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational metric observations exposed by $S$.
\item $R$ is the terminal $\RealUp$ seal for all distance and tolerance rows.
\item $H$ records componentwise $\hsame$ transport for the metric, compact, totally bounded, continuity, graph-agreement, separated-target, inverse-modulus, stream, regular-rational, Real, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
X,Y,M,T,F,G,A,B,E,S,Q,R \longmapsto \NameCert_{\CompactUniformHomeomorphismUp}.
$$
\item $P$ is the $\Pkg$ provenance over $\CompactUniformHomeomorphismUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\MetricSpaceUp$, $\TotallyBoundedUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactUniformHomeomorphismUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,Y,M,T,F,G,A,B,E,S,Q,R,H,C,P,N$. The carrier has no coordinate for open-cover compactness, selected nearest net points, quotient equality of functions, host equality, an ambient inverse map, choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CompactUniformHomeomorphism NameCert surface]\label{thm:compact-uniform-homeomorphism-namecert-surface}
For every accepted $\CompactUniformHomeomorphismUp$ carrier
$$
U=(X,Y,M,T,F,G,A,B,E,S,Q,R,H,C,P,N),
$$
the local $\NameCert_{\CompactUniformHomeomorphismUp}$ surface consists exactly of the metric-space rows $X,Y$, the compact-metric finite-cover row $M$, the totally-bounded finite-net row $T$, the forward and inverse graph rows $F,G,A$, the separated-target ledger $B$, the inverse-modulus row $E$, the finite stream and regular-rational rows $S,Q$, the terminal Real seal $R$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local name $N$.

Consequently every inverse-uniform-continuity read exported by the packet must pass through the sibling $\CompactMetricUp$, $\ContinuousMapUp$, $\MetricSpaceUp$, $\TotallyBoundedUp$, and $\RealUp$ rows before any consumer may inspect the inverse modulus. The surface exports no open-cover compactness theorem, no selected finite subcover, no quotient equality of maps, no host equality, no choice function, and no ambient Real-completeness witness.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its public rows are precisely the metric, compact, total-boundedness, continuity, graph-agreement, separation, modulus, stream, regular-rational, Real, transport, replay, provenance, and local naming rows listed in \autoref{def:compact-uniform-homeomorphism-carrier}.

The finite-net rows are read from $M$ through $T$, while the map rows are read from $F,G,A$. The separated-target ledger $B$ compares finite target cells using only the metric classifier rows in $Y$ and the displayed forward graph row.

The inverse-modulus row $E$ is downstream of those finite rows. Transport, replay, provenance, and local naming are then supplied by $H,C,P,N$ without adding another compactness or equality coordinate.
\end{proof}

\begin{theorem}[CompactUniformHomeomorphism inverse modulus]\label{thm:compact-uniform-homeomorphism-inverse-modulus}
Let $U$ be an accepted $\CompactUniformHomeomorphismUp$ packet and let $\varepsilon$ be a positive target tolerance row displayed through the target $\MetricSpaceUp$ and $\RealUp$ seal. Then $U$ displays a finite source tolerance row $\delta$ such that every pair of target observations whose source representatives are read through the accepted inverse graph row and whose target distance is below $\delta$ has source distance below $\varepsilon$ on the displayed finite windows.

The row $\delta$ is obtained by refining the $\TotallyBoundedUp$ finite-net row of the $\CompactMetricUp$ source until the separated-target ledger accepts the target tolerance. It preserves the $\ContinuousMapUp$ graph rows, $\MetricSpaceUp$ distance rows, $\RealUp$ tolerance seal, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ support. The construction does not use choice, open-cover compactness, host equality, quotient equality of maps, selected limits, or ambient Real completeness.
\end{theorem}
\begin{proof}
Start with the positive target tolerance row and open the finite-net row $T$ supplied by the compact-metric source row $M$. Each refinement remains a displayed finite BEDC row with the same metric, stream, regular-rational, and Real seal support.

Use the separated-target ledger $B$ to test the images of the finitely many source cells. When the ledger accepts the requested target separation, it records a finite source radius that prevents two distinct source cells from being identified by the inverse graph read.

Read that accepted radius as the inverse-modulus row $E$. The forward and inverse graph rows $F,G,A$ then transport the finite target comparison back to the source metric rows, and $H,C,P,N$ preserve the same route under transport, replay, provenance, and local naming.

Since every step uses displayed finite-net rows and separated-target rows, the modulus is not extracted from a choice operator, an open-cover compactness proof, host equality, quotient map equality, selected limits, or ambient Real completeness.
\end{proof}

\falsifiablePrediction{Every $\CompactUniformHomeomorphismUp$ inverse-modulus read factors through one CompactMetric finite-cover row, one TotallyBounded finite-net row, ContinuousMap graph rows, MetricSpace distance rows, RealUp tolerance seals, separated-target rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{compactmetric, continuousmap, metricspace, totallybounded, real: $\CompactUniformHomeomorphismUp$ is not bijective to any listed sibling because it jointly carries finite-net refinement, separated-target comparison, inverse graph agreement, inverse-modulus extraction, Real tolerance sealing, transport, replay, provenance, and local naming as one certificate.}

\closureat{CompactUniformHomeomorphismUp}{seedStr}

\begin{closurestatus}{\CompactUniformHomeomorphismUp}
  \constructivestory{A $\CompactUniformHomeomorphismUp$ packet is generated from source and target MetricSpace rows, CompactMetric finite-cover data, TotallyBounded finite-net rows, ContinuousMap graph rows, separated-target comparison, inverse graph agreement, inverse-modulus extraction, stream and regular-rational readback, Real tolerance sealing, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-homeomorphism-carrier}, \autoref{thm:compact-uniform-homeomorphism-namecert-surface}, and \autoref{thm:compact-uniform-homeomorphism-inverse-modulus} seed the finite compact-uniform-homeomorphism carrier, certificate, and inverse-modulus surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close open-cover compactness, selected finite subcovers, quotient equality of functions or maps, host equality, choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net refinement exactness, separated-target ledger exactness, inverse graph agreement, inverse-modulus extraction and non-escape, transport, replay, provenance, local naming, package non-escape, and a Lean carrier formalization for BEDC.Derived.CompactUniformHomeomorphismUp.}
\end{closurestatus}
