\chapter{A Concrete Naming Certificate for $\HopfRinowFiniteGeodesicUp$}
\label{ch:concrete-instances-hopf-rinow-finite-geodesic-namecert}
\origin{human}

Following Hopf and Rinow, the $\HopfRinowFiniteGeodesicUp$ packet records the finite BEDC surface on which a compact complete Riemannian metric presentation exposes geodesic segments only as named rows. It reads the complete-metric handoff of \autoref{ch:concrete-instances-completemetric-namecert}, the geodesic metric surface of \autoref{ch:concrete-instances-geodesic-metric-namecert}, the Riemannian metric row of \autoref{ch:concrete-instances-riemannianmetric-namecert}, the compact metric row of \autoref{ch:concrete-instances-compactmetric-namecert}, and the Real readback boundary of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite geodesic NameCert neighbour for completion data; it does not assert classical compactness theorems, select minimizing geodesics globally, or import ambient $\RealUp$ completeness.

\begin{definition}[Hopf--Rinow finite geodesic carrier]
\label{def:hopf-rinow-finite-geodesic-carrier}
A $\HopfRinowFiniteGeodesicUp$ carrier is a finite $\BHist$ packet
$$
G=(C,M,R,K,S,Q,A,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the $\CompleteMetricUp$ row exposing the Cauchy-limit service used by finite geodesic endpoint reads.
\item $M$ is the $\GeodesicMetricUp$ row naming the displayed geodesic segment incidence surface.
\item $R$ is the $\RiemannianMetricUp$ row whose tangent-fibre metric data supplies the local length ledger.
\item $K$ is the $\CompactMetricUp$ row whose finite-net and coverage witnesses bound the inspected endpoint windows.
\item $S$ is the $\StreamNameUp$ row listing the endpoint, subdivision, and observation windows opened by the packet.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational length, radius, and tolerance observations exposed by $S$.
\item $A$ is the $\RealUp$ seal for the finite distance and length comparisons read through $Q$.
\item $H$ records componentwise $\hsame$ transport for the complete, geodesic, Riemannian, compact, stream, readback, Real, replay, provenance, and naming rows.
\item $T$ records displayed $\Cont$ replay from endpoint windows through geodesic incidence, finite length comparisons, compact coverage, and complete-metric handoff.
\item $P$ is the $\Pkg$ provenance over $\HopfRinowFiniteGeodesicUp$, $\CompleteMetricUp$, $\GeodesicMetricUp$, $\RiemannianMetricUp$, $\CompactMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HopfRinowFiniteGeodesicUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an open-cover compactness theorem, a global minimizing-geodesic selector, quotient path equality, an unbounded Hopf--Rinow equivalence, or ambient $\RealUp$ completeness outside the displayed finite readback route.
\end{definition}

\begin{theorem}[Hopf--Rinow finite geodesic NameCert obligations]
\label{thm:hopf-rinow-finite-geodesic-namecert-obligations}
For every accepted $\HopfRinowFiniteGeodesicUp$ carrier $G=(C,M,R,K,S,Q,A,H,T,P,N)$, the local $\NameCert_{\HopfRinowFiniteGeodesicUp}$ surface consists exactly of carrier admission for the complete-metric row, geodesic-metric incidence row, Riemannian metric row, compact-metric row, finite stream windows, regular-rational readback, Real comparison seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every finite geodesic read must expose $C,M,R,K,S,Q,A,H,T,P,N$ before it can be consumed by a completion or metric-geometry neighbour.

The packet exports no classical Hopf--Rinow equivalence, no chosen minimizing geodesic for arbitrary endpoints, no open-cover compactness principle, no quotient path completion, and no ambient completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hopf-rinow-finite-geodesic-carrier}. The complete, geodesic, Riemannian, and compact faces occur only as the rows $C,M,R,K$, so a downstream reader cannot replace them by host compactness or a global geodesic theorem.

Read the finite observations through $S,Q,A$. The stream row displays the endpoint and subdivision windows, the regular-rational row reads the length and radius comparisons opened by those windows, and the Real row seals only those finite comparisons.

The structural rows $H,T,P,N$ then transport, replay, source, and name the same packet. Since no other coordinate occurs in the carrier, the local NameCert obligations cannot import open-cover compactness, a selected minimizing-geodesic function, quotient path equality, an unbounded Hopf--Rinow equivalence, or ambient Real completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\HopfRinowFiniteGeodesicUp$ finite geodesic read factors through displayed CompleteMetricUp, GeodesicMetricUp, RiemannianMetricUp, CompactMetricUp, StreamNameUp, RegSeqRatUp, RealUp, hsame, Cont, Pkg, and local NameCert rows.}

\independenceWitness{completemetric, geodesic-metric, riemannianmetric, compactmetric, streamname, regseqrat, real: $\HopfRinowFiniteGeodesicUp$ is not bijective to any listed sibling because it carries the finite geodesic endpoint route together with completion, compact coverage, Riemannian length, rational readback, and local naming rows in one packet.}

\closureat{HopfRinowFiniteGeodesicUp}{seedStr}

\begin{closurestatus}{\HopfRinowFiniteGeodesicUp}
  \constructivestory{A $\HopfRinowFiniteGeodesicUp$ packet is generated from CompleteMetricUp handoff rows, GeodesicMetricUp incidence rows, RiemannianMetricUp length rows, CompactMetricUp finite-net rows, StreamName endpoint windows, RegSeqRat readback, RealUp comparison seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hopf-rinow-finite-geodesic-carrier} and \autoref{thm:hopf-rinow-finite-geodesic-namecert-obligations} seed the finite geodesic NameCert surface over completion, compactness, Riemannian metric, and rational readback rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim the classical Hopf--Rinow theorem, global minimizing geodesic selection, open-cover compactness, quotient path completion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite endpoint-window replay, geodesic incidence stability, Riemannian length readback, compact coverage routing, complete-metric handoff, Real comparison exactness, transport, replay, provenance, and local naming for BEDC.Derived.HopfRinowFiniteGeodesicUp.}
\end{closurestatus}
