\chapter{A Concrete Naming Certificate for $\LocatedMonotoneLimitUp$}
\label{ch:concrete-instances-located-monotone-limit-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedMonotoneLimitUp$ packet records the finite route by which a located upper bound and a displayed monotone real sequence supply a regular Cauchy seal without importing a classical supremum, trichotomy, countable choice, or ambient $\RealUp$ completeness. It sits after the reusable upper-bound witness of \autoref{ch:concrete-instances-located-upper-bound-namecert}, the located-supremum monotone handoff of \autoref{ch:concrete-instances-locatedsupremum-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[LocatedMonotoneLimit carrier]
\label{def:located-monotone-limit-carrier}
A $\LocatedMonotoneLimitUp$ carrier is a finite $\BHist$ packet
$$
M=(S,D,U,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the monotone real-sequence row, carrying the inspected finite sequence windows and the displayed increasing comparison ledger.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row attached to those finite windows.
\item $U$ is the $\LocatedUpperBoundUp$ row, naming the located upper-bound witness consumed by the sequence window.
\item $W$ is the common precision-window row, recording the finite index at which the monotone window and upper-bound ledger are read together.
\item $R$ is the $\RegSeqRatUp$ readback row extracted from $S,D,U,W$.
\item $E$ is the terminal $\RealUp$ seal row reached from the regular readback $R$ and from no other source.
\item $H$ records componentwise $\hsame$ transport for the monotone sequence, dyadic tolerance, located upper bound, common window, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from every limit request through $S,D,U,W,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedMonotoneLimitUp$, $\LocatedUpperBoundUp$, $\LocatedSupremumUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedMonotoneLimitUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host supremum, a selected limit point, quotient real equality, trichotomy, countable choice, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[LocatedMonotoneLimit NameCert obligations]
\label{thm:located-monotone-limit-namecert-obligations}
For every accepted $\LocatedMonotoneLimitUp$ carrier
$$
M=(S,D,U,W,R,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedMonotoneLimitUp}$ surface consists exactly of carrier admission, monotone-window exposure, located-upper-bound extraction, common-window compatibility, regular Cauchy readback, terminal Real-seal routing, componentwise transport, displayed replay, provenance, and local naming for the same finite packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-monotone-limit-carrier}. The analytic rows visible before the seal are exactly the monotone sequence row $S$, dyadic tolerance row $D$, located upper-bound row $U$, common precision window $W$, and regular readback row $R$.

The located-upper-bound and monotone-window obligations are read before $R$. Thus the regular Cauchy readback is built from displayed finite rows rather than from a host supremum theorem or a selected limit.

Finally read the structural rows $H,C,P,N$. They transport, replay, source, and name the same packet componentwise, so the listed obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[LocatedMonotoneLimit upper-bound extraction]
\label{thm:located-monotone-limit-upper-bound-extraction}
Every accepted $\LocatedMonotoneLimitUp$ carrier exposes its upper-bound information only through the displayed $\LocatedUpperBoundUp$ row $U$ and the common precision window $W$. A completion-facing consumer must read $S,D,U,W$ before it can inspect the regular readback $R$ or the terminal Real seal $E$.
\end{theorem}
\begin{proof}
The upper-bound coordinate of the carrier is the row $U$. By definition it is paired with the monotone sequence and tolerance rows through the window $W$, so no consumer can read an upper-bound witness detached from the inspected sequence window.

The readback row $R$ is downstream of $S,D,U,W$. Therefore any completion-facing request that reaches $R$ or $E$ has already exposed the located upper-bound witness and the finite precision window that binds it to the monotone sequence.
\end{proof}

\begin{theorem}[LocatedMonotoneLimit regular Cauchy seal]
\label{thm:located-monotone-limit-regular-cauchy-seal}
Every $\RealUp$-facing read exported by an accepted $\LocatedMonotoneLimitUp$ carrier factors through the finite route
$$
S,D,U,W \longmapsto R \longmapsto E \longmapsto H,C,P,N.
$$
The route records the constructive monotone-limit handoff as a regular rational Cauchy seal, not as a quotient completion, selected supremum, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the displayed monotone sequence, dyadic tolerance ledger, located upper-bound row, and common precision window. These rows are the only pre-readback coordinates of the carrier.

The row $R$ repacks those finite rows as regular rational Cauchy data. The terminal row $E$ is then a $\RealUp$ seal for that readback, and $H,C,P,N$ preserve the same route under transport, replay, provenance, and naming.

Since the carrier has no quotient-completion, selected-supremum, or ambient-completeness coordinate, the exported seal is exactly the displayed regular Cauchy route.
\end{proof}

\begin{theorem}[LocatedMonotoneLimit nonescape]
\label{thm:located-monotone-limit-nonescape}
No accepted $\LocatedMonotoneLimitUp$ consumer can extract a classical least upper bound, trichotomy decision, countable-choice selector, quotient representative, host sequence equality, or ambient $\RealUp$ completeness principle from the packet. Every observable limit-facing row remains a read of $S,D,U,W,R,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. They list only the monotone sequence windows, dyadic tolerance ledger, located upper-bound witness, common precision window, regular readback, terminal seal, and structural rows.

The refused objects are absent from this list. Componentwise transport through $H$ and replay through $C$ preserve existing rows but do not add new coordinates, and provenance plus local naming record the same finite packet.

Consequently any accepted consumer remains inside the route $S,D,U,W,R,E,H,C,P,N$ and cannot export the refused classical or ambient data.
\end{proof}

\closureat{LocatedMonotoneLimitUp}{seedStr}

\begin{closurestatus}{\LocatedMonotoneLimitUp}
  \constructivestory{A $\LocatedMonotoneLimitUp$ packet is generated from monotone real-sequence windows, a DyadicRatCore tolerance ledger, a LocatedUpperBound witness, a common precision window, RegSeqRat readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-monotone-limit-carrier}, \autoref{thm:located-monotone-limit-namecert-obligations}, \autoref{thm:located-monotone-limit-upper-bound-extraction}, \autoref{thm:located-monotone-limit-regular-cauchy-seal}, and \autoref{thm:located-monotone-limit-nonescape} seed the finite constructive monotone-limit handoff from located upper-bound data to a regular Cauchy Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close classical supremum existence, trichotomy, countable choice, quotient representatives, host sequence equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, monotone-window exposure, located-upper-bound extraction, common-window compatibility, regular Cauchy readback, Real-seal routing, transport, replay, provenance, and local naming for BEDC.Derived.LocatedMonotoneLimitUp.}
\end{closurestatus}
