\chapter{A Concrete Naming Certificate for $\KolmogorovQuotientUp$}
\label{ch:concrete-instances-kolmogorov-quotient-namecert}
\origin{human}

Following Kolmogorov and Bourbaki's separation discipline for topological spaces, the $\KolmogorovQuotientUp$ packet records the constructive $T_0$ reflection as finite observable-open data rather than as a host quotient object. It sits next to the indexed-open topology of \autoref{ch:concrete-instances-topology-namecert}, the metric-generated topology route of \autoref{ch:concrete-instances-metric-namecert}, the membership discipline of \autoref{ch:concrete-instances-setlike-namecert}, and the specialization reflection packet of \autoref{ch:concrete-instances-tzero-reflection-namecert}. The packet names indistinguishability by mutual observable-open evidence and exposes a separated carrier only through displayed representative rows.

\begin{definition}[Kolmogorov quotient carrier]
\label{def:kolmogorov-quotient-carrier}
A $\KolmogorovQuotientUp$ carrier is a finite $\BHist$ packet
$$
K=(T,O,E,R,S,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $T$ is the $\TopologyUp$ indexed-open row, carrying the open indices and membership reads used to test observable separation.
\item $O$ is the observable-open classifier row, recording for each displayed point row which indexed opens are observed as present.
\item $E$ is the indistinguishability ledger: two point rows are equivalent for this packet exactly when every observable-open row in $O$ agrees in both directions.
\item $R$ is the representative-display row. It records a finite public name for an $E$-class but does not select a host representative by choice.
\item $S$ is the separated-reader row. It exposes a $T_0$ read only after $E$ and $R$ have been displayed, so separated equality is mutual observable-open agreement.
\item $H$ records componentwise $\hsame$ transport for $T,O,E,R,S$ and the structural rows.
\item $C$ records $\Cont$ replay from a topology request through observable opens, indistinguishability, representative display, and separated reading.
\item $P$ is the $\Pkg$ provenance over $\KolmogorovQuotientUp$, $\TopologyUp$, $\MetricSpaceUp$, $\TZeroReflectionUp$, $\SetLikeUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\KolmogorovQuotientUp}$ row.
\end{enumerate}
The carrier has no coordinate for a quotient primitive, proof irrelevance over opens, selected representative function, ambient set quotient, powerset extensionality, or excluded-middle split of points.
\end{definition}

\begin{definition}[Kolmogorov quotient classifier]
\label{def:kolmogorov-quotient-classifier}
For an accepted carrier $K=(T,O,E,R,S,H,C,P,N)$, the displayed classifier on public quotient names is the finite route
$$
O,E,R,S \longmapsto H,C,P,N .
$$
Two public names classify as the same $\KolmogorovQuotientUp$ point only when their observable-open rows agree through $E$, their displayed representative rows are preserved by $H$, and their separated reads replay through $C$ under the same provenance and local name rows.
\end{definition}

\begin{theorem}[Kolmogorov quotient NameCert obligations]
\label{thm:kolmogorov-quotient-namecert-obligations}
For every accepted $\KolmogorovQuotientUp$ carrier $K=(T,O,E,R,S,H,C,P,N)$, the local $\NameCert_{\KolmogorovQuotientUp}$ surface consists exactly of topology-source admission through $T$, observable-open classifier exposure through $O$, mutual-observation indistinguishability through $E$, representative-display exposure through $R$, separated-reader exposure through $S$, componentwise $\hsame$ stability through $H$, $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:kolmogorov-quotient-carrier}. The only topology data available to the packet is the indexed-open row $T$ and its observable classifier $O$.

The indistinguishability row $E$ is therefore forced to compare point rows by observable-open agreement. The representative-display row $R$ records public names for such rows, but it has no host choice coordinate from which to select representatives.

The separated-reader row $S$ can be consumed only after $E$ and $R$ have been exposed. Componentwise transport $H$, replay $C$, provenance $P$, and local naming $N$ preserve that same route, so every NameCert obligation is one of the displayed rows and no quotient primitive or ambient set identification is added.
\end{proof}

\begin{theorem}[Kolmogorov quotient T0 reflection]
\label{thm:kolmogorov-quotient-tzero-reflection}
Every separated consumer of an accepted $\KolmogorovQuotientUp$ packet factors through the finite reflection route
$$
\TopologyUp \longmapsto \KolmogorovQuotientUp \longmapsto \TZeroReflectionUp .
$$
Thus the consumer may distinguish public quotient names exactly by observable-open disagreement and may identify them only by the mutual-observation row $E$ transported through $H,C,P,N$.
\end{theorem}
\begin{proof}
Start with the topology row $T$ and observable classifier $O$. These rows determine which opens are visible at each displayed point row.

Use the indistinguishability ledger $E$. If every observable-open read agrees in both directions, the packet admits the same public quotient name through $R$; if a displayed open separates the rows, the separated-reader row $S$ records the $T_0$ distinction.

Finally replay the structural tail. The rows $H,C,P,N$ keep the observable-open route fixed, and the sibling $\TZeroReflectionUp$ packet of \autoref{ch:concrete-instances-tzero-reflection-namecert} consumes precisely the separated specialization surface. No quotient primitive, selected representative, or powerset equality participates in the reflection.
\end{proof}

\begin{theorem}[Kolmogorov quotient metric-source compatibility]
\label{thm:kolmogorov-quotient-metric-source-compatibility}
If a $\MetricSpaceUp$ source supplies the topology row $T$ through the metric-generated route of $\TopologyUp$, then every $\KolmogorovQuotientUp$ separated read still factors through the same observable-open rows $O,E,R,S,H,C,P,N$. The metric source contributes open-ball observations; it does not add a second equality on quotient names, a Cauchy-completion selector, or a Hausdorff quotient of points.
\end{theorem}
\begin{proof}
Read the metric source only through the topology handoff. The metric carrier may generate basic open rows, but the $\KolmogorovQuotientUp$ packet consumes them as the indexed-open row $T$.

The observable classifier $O$ and indistinguishability row $E$ then perform the same mutual-open test as in the purely topological case. The rows $R$ and $S$ expose public quotient names and $T_0$ separation only after this test.

The structural rows $H,C,P,N$ preserve the same route. Since no additional metric equality row belongs to the carrier, a metric source cannot replace observable-open indistinguishability by a host metric quotient or completion-side selector.
\end{proof}

\falsifiablePrediction{A claimed $\KolmogorovQuotientUp$ read that identifies public names without displaying $T,O,E,R,S,H,C,P,N$, or that selects a representative by a host choice function, refutes the carrier of \autoref{def:kolmogorov-quotient-carrier}.}

\independenceWitness{topology, metricspace, tzero-reflection, setlike: $\KolmogorovQuotientUp$ is not bijective to any listed sibling because it carries the joint observable-open indistinguishability ledger, representative-display row, separated-reader row, and non-quotient NameCert route. TopologyUp supplies indexed opens without the separated public-name row; MetricSpaceUp supplies distance-generated opens without a quotient-name surface; TZeroReflectionUp consumes specialization separation without this representative-display ledger; SetLikeUp supplies membership discipline without topological observability.}

\closureat{KolmogorovQuotientUp}{seedStr}

\begin{closurestatus}{\KolmogorovQuotientUp}
  \constructivestory{A $\KolmogorovQuotientUp$ packet is generated from a Topology indexed-open row, observable-open classifier, mutual-observation indistinguishability ledger, representative-display row, separated-reader row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kolmogorov-quotient-carrier}, \autoref{def:kolmogorov-quotient-classifier}, \autoref{thm:kolmogorov-quotient-namecert-obligations}, and \autoref{thm:kolmogorov-quotient-tzero-reflection} seed the finite constructive $T_0$ reflection surface without quotient primitives.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a host quotient object, selected representatives, proof irrelevance over opens, ambient powerset extensionality, excluded middle over points, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, observable-open exactness, mutual-observation stability, representative-display coverage, separated-reader exactness, and sibling handoff for BEDC.Derived.KolmogorovQuotientUp.}
\end{closurestatus}
