\chapter{A Concrete Naming Certificate for $\FiniteRealSupremumUp$}
\label{ch:concrete-instances-finite-real-supremum-namecert}
\origin{human}

Following Bishop and Bridges, the $\FiniteRealSupremumUp$ packet records the finite upper-bound search used when a nonempty finite family of constructive real names must expose a supremum row before any compact finite-net or finite-bound consumer can read it. It sits over the rational arithmetic base of \autoref{ch:concrete-instances-rat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the displayed comparison discipline of \autoref{ch:concrete-instances-totalorder-namecert}, the binary min--max sibling of \autoref{ch:concrete-instances-real-min-max-namecert}, and the finite-net fold route of \autoref{ch:concrete-instances-finitenetminimumfold-namecert}. The packet names finite supremum data only; it does not import host maximum, quotient real equality, order trichotomy, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Finite real supremum carrier]
\label{def:finite-real-supremum-carrier}
A $\FiniteRealSupremumUp$ carrier is a finite $\BHist$ packet
$$
S=(R,I,O,M,U,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the nonempty finite $\RealUp$ packet, listing the real-name rows retained by the supremum request together with their finite index witnesses.
\item $I$ is the inhabitedness row, exposing the selected starting index and its $\RealUp$ name before any comparison ledger is read.
\item $O$ is the finite comparison ledger, recording the $\TotalOrderUp$ comparison rows used to compare retained $\RealUp$ names through rational readback and displayed order witnesses.
\item $M$ is the $\RealMinMaxUp$ fold ledger, showing how the finite comparison rows select the displayed upper-bound candidate from the retained real rows.
\item $U$ is the selected upper-bound row, asserting that every retained member of $R$ is bounded above by the candidate selected through $M$ and $O$.
\item $L$ is the least-bound verification row, asserting that every displayed upper bound for $R$ receives a comparison witness from the selected candidate into that bound.
\item $H$ records componentwise $\hsame$ transport for the finite real packet, inhabitedness row, comparison ledger, fold ledger, upper-bound row, least-bound row, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a finite-supremum request through $R,I,O,M,U,L,H$.
\item $P$ is the $\Pkg$ provenance over $\FiniteRealSupremumUp$, $\RealUp$, $\RatUp$, $\TotalOrderUp$, $\RealMinMaxUp$, $\FiniteNetMinimumFoldUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FiniteRealSupremumUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host maximum operator, quotient-real equality, detached order trichotomy, selected limit outside the finite packet, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Finite real supremum NameCert obligations]
\label{thm:finite-real-supremum-namecert-obligations}
For every accepted $\FiniteRealSupremumUp$ carrier
$$
S=(R,I,O,M,U,L,H,C,P,N),
$$
the local $\NameCert_{\FiniteRealSupremumUp}$ surface consists exactly of carrier admission for the nonempty finite $\RealUp$ packet $R$, inhabitedness exposure through $I$, finite $\TotalOrderUp$ comparison-ledger access through $O$, $\RealMinMaxUp$ fold selection through $M$, selected upper-bound verification through $U$, least-bound verification through $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-real-supremum-carrier}. The row $R$ gives the finite list of real-name rows, and $I$ keeps the packet nonempty before any upper-bound request is considered.

The comparison and selection rows are read next. The ledger $O$ exposes only displayed $\TotalOrderUp$ comparison witnesses over the retained $\RealUp$ rows, while $M$ records the finite $\RealMinMaxUp$ fold that selects the candidate read by the upper-bound row.

The bounding rows are downstream of that fold. The row $U$ checks that every retained real row is below the selected candidate, and $L$ checks that any displayed upper bound receives a comparison witness from the selected candidate.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no row carries host maximum, quotient-real equality, detached trichotomy, countable choice, open-cover compactness, or ambient completeness, the listed rows exhaust the local NameCert surface.
\end{proof}

\falsifiablePrediction{An accepted $\FiniteRealSupremumUp$ consumer that reads a supremum row without first displaying the nonempty finite $\RealUp$ packet, comparison ledger, selected upper-bound row, least-bound verification row, transport, replay, provenance, and local naming refutes the carrier surface.}

\independenceWitness{real, rat, total-order, real-min-max, finitenetminimumfold: no listed sibling is bijective with $\FiniteRealSupremumUp$ because this packet jointly carries a nonempty finite RealUp family, a finite comparison ledger, an upper-bound candidate, a least-bound verification row, componentwise transport, replay, provenance, and a local $\NameCert$ row.}

\closureat{FiniteRealSupremumUp}{seedStr}

\begin{closurestatus}{\FiniteRealSupremumUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-real-supremum-carrier} and \autoref{thm:finite-real-supremum-namecert-obligations} seed the finite supremum route through nonempty Real rows, comparison ledgers, selected upper-bound rows, least-bound verification, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host maximum, quotient Real equality, detached order trichotomy, selected limits outside the finite packet, countable choice, open-cover compactness, Lean verification, bridge checking, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, nonempty finite Real packet exposure, comparison-ledger exactness, selected upper-bound verification, least-bound verification, and TasteGate compatibility for BEDC.Derived.FiniteRealSupremumUp.}
  \constructivestory{A $\FiniteRealSupremumUp$ packet is generated from a nonempty finite RealUp packet, finite TotalOrderUp comparison rows, a RealMinMaxUp fold ledger, an upper-bound row, a least-bound verification row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
\end{closurestatus}
