\chapter{A Concrete Naming Certificate for $\ProfiniteCompletionUp$}
\label{ch:concrete-instances-profinite-completion-namecert}
\origin{human}

Following Serre and Bourbaki-style profinite completion, the $\ProfiniteCompletionUp$ packet records a residually finite completion surface as finite inverse-limit quotient data rather than as a host topological group. It consumes the projection-window discipline of \autoref{ch:concrete-instances-inverse-limit-metric-namecert}, the binary compact readback of \autoref{ch:concrete-instances-cantorspace-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, and the compact metric witness surface of \autoref{ch:concrete-instances-compactmetric-namecert}. The packet names only finite quotient stages, finite projection checks, compact totally disconnected readbacks, transport, replay, provenance, and local naming; it refuses quotient completion, Haar measure, selected infinite points, host equality, and choice.

\begin{definition}[Profinite completion carrier]
\label{def:profinite-completion-carrier}
A $\ProfiniteCompletionUp$ carrier is a finite $\BHist$ packet
$$
F=(Q,\Pi,W,B,K,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the quotient-stage ledger. Each row names a visible finite quotient stage, its finite kernel witness, and the finite comparison data admitted at that stage.
\item $\Pi$ is the projection-compatibility ledger. It records only finite bonding maps between named quotient stages and the checked compatibility rows consumed by the inverse-limit surface.
\item $W$ is the $\StreamNameUp$ finite-window row by which consumers ask for finitely many quotient stages and finitely many projection comparisons.
\item $B$ is the $\CantorSpaceUp$ readback row for the compact totally disconnected binary presentation obtained from the displayed finite windows.
\item $K$ is the $\CompactMetricUp$ readback row, sealing the compact metric surface reached through the same finite quotient and projection data.
\item $H$ records componentwise $\hsame$ transports for quotient stages, projection compatibility rows, stream windows, Cantor-space readbacks, compact metric readbacks, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay of the route
$$
Q\longmapsto \Pi\longmapsto W\longmapsto B\longmapsto K .
$$
\item $P$ is the $\Pkg$ provenance over $\ProfiniteCompletionUp$, $\InverseLimitMetricUp$, $\CantorSpaceUp$, $\StreamNameUp$, $\CompactMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ProfiniteCompletionUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion, Haar measure, selected infinite points, host equality, or choice.
\end{definition}

\begin{theorem}[Profinite completion NameCert obligations]
\label{thm:profinite-completion-namecert-obligations}
For every accepted $\ProfiniteCompletionUp$ carrier $F=(Q,\Pi,W,B,K,H,C,P,N)$, the local $\NameCert_{\ProfiniteCompletionUp}$ surface consists exactly of carrier admission for the displayed quotient-stage ledger, finite projection-compatibility ledger, $\StreamNameUp$ finite windows, $\CantorSpaceUp$ compact totally disconnected readback, $\CompactMetricUp$ readback, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every public read must pass through those rows in the order displayed by $C$.
\end{theorem}
\begin{proof}
Project the accepted carrier in \autoref{def:profinite-completion-carrier}. The only mathematical rows available to a consumer are the finite quotient stages $Q$, the projection-compatibility ledger $\Pi$, the finite window schedule $W$, the Cantor-space readback $B$, and the compact metric readback $K$.

The replay row $C$ fixes the inspection route. A public read first selects finitely many quotient stages, then verifies finite projection compatibility, then reads the StreamName window, and only then reaches the CantorSpace and CompactMetric readback rows.

The rows $H,P,N$ transport, source, and name exactly that surface. Since the carrier has no coordinate for quotient completion, Haar measure, selected infinite points, host equality, or choice, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Profinite completion inverse-limit route]
\label{thm:profinite-completion-inverse-limit-route}
Every inverse-limit-facing read exported by an accepted $\ProfiniteCompletionUp$ carrier factors through the displayed route
$$
Q,\Pi,W,B,K,H,C,P,N .
$$
The quotient-stage ledger $Q$ supplies finite stage data, $\Pi$ supplies finite bonding compatibility, $W$ supplies the $\StreamNameUp$ window discipline, $B$ supplies the $\CantorSpaceUp$ compact totally disconnected readback, and $K$ supplies the $\CompactMetricUp$ readback. The rows $H,C,P,N$ provide transport, replay, provenance, and local naming for the same route.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:profinite-completion-carrier}. Its inverse-limit content is not a host object; it is the displayed finite route from quotient stages and projection checks to finite windows and compact readbacks.

Apply the NameCert surface of \autoref{thm:profinite-completion-namecert-obligations}. The consumer must inspect $Q$ and $\Pi$ before reading $W$, and $W$ is the only access path to the CantorSpace row $B$ and the CompactMetric row $K$.

Transport by $H$ and replay by $C$ preserve the same finite route, while $P$ and $N$ record provenance and local naming. Therefore every inverse-limit-facing read factors through $Q,\Pi,W,B,K,H,C,P,N$ and exports no quotient completion, Haar measure, selected infinite point, host equality, or choice principle.
\end{proof}

\closureat{ProfiniteCompletionUp}{seedStr}

\begin{closurestatus}{\ProfiniteCompletionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:profinite-completion-carrier}, \autoref{thm:profinite-completion-namecert-obligations}, and \autoref{thm:profinite-completion-inverse-limit-route} seed the finite profinite-completion packet over quotient stages, projection compatibility, StreamName windows, CantorSpace readback, CompactMetric readback, transport, replay, provenance, and naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completion, Haar measure, selected infinite points, host equality, choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite quotient-stage routing, projection compatibility, StreamName window routing, CantorSpace readback, CompactMetric readback, transport stability, provenance, and local naming for BEDC.Derived.ProfiniteCompletionUp.}
  \constructivestory{A $\ProfiniteCompletionUp$ packet is generated from finite quotient-stage rows, projection-compatibility rows, StreamName finite-window rows, CantorSpace compact totally disconnected readback rows, CompactMetric readback rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
\end{closurestatus}
