\chapter{A Concrete Naming Certificate for $\FiniteRealIntervalChainUp$}
\label{ch:concrete-instances-finite-real-interval-chain-namecert}
\origin{human}

Following Cantor and Bishop--Bridges constructive nested-interval practice, the $\FiniteRealIntervalChainUp$ packet records a finite real-interval chain before any Real or Completion consumer may read an endpoint route as a point-name witness. It sits beside the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the located nested-interval sibling of \autoref{ch:concrete-instances-located-real-nested-intervals-namecert}. The packet names finite endpoint ledgers, containment witnesses, and diameter budgets; it is not an open-cover compactness theorem, a quotient-real construction, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Finite real interval chain carrier]
\label{def:finite-real-interval-chain-carrier}
A $\FiniteRealIntervalChainUp$ carrier is a finite $\BHist$ packet
$$
F=(E,I,J,D,S,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the endpoint ledger, listing the left and right endpoint rows for each retained interval cell and their $\RealUp$-facing names.
\item $I$ is the closed interval row family, recording the displayed closed interval cells and their endpoint order witnesses.
\item $J$ is the chain containment witness row, asserting that every later interval cell is read inside the preceding cell through finite endpoint comparisons.
\item $D$ is the $\DyadicRatCoreUp$ diameter-budget row, carrying the requested dyadic tolerance and the displayed diameter bound for each retained cell.
\item $S$ is the $\StreamNameUp$ window row through which endpoint and containment observations are requested.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the same windows and dyadic budget ledgers.
\item $L$ is the terminal $\RealUp$ seal row reached only after $E,I,J,D,S,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for endpoint ledgers, closed interval rows, containment witnesses, dyadic budgets, stream windows, readback, Real seal, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a Real-facing interval witness request through $E,I,J,D,S,R,L,H$.
\item $P$ is the $\Pkg$ provenance over $\FiniteRealIntervalChainUp$, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, \autoref{ch:concrete-instances-real-namecert}, \autoref{ch:concrete-instances-located-real-nested-intervals-namecert}, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FiniteRealIntervalChainUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for host interval intersection, selected quotient representatives, countable choice, open-cover compactness, detached completion data, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[FiniteRealIntervalChain NameCert obligations]
\label{thm:finite-real-interval-chain-namecert-obligations}
For every accepted $\FiniteRealIntervalChainUp$ carrier $F=(E,I,J,D,S,R,L,H,C,P,N)$, the local $\NameCert_{\FiniteRealIntervalChainUp}$ surface consists exactly of endpoint-ledger admission through $E$, closed interval row exposure through $I$, chain-containment witnesses through $J$, dyadic diameter budgets through $D$, $\StreamNameUp$ window access through $S$, $\RegSeqRatUp$ readback through $R$, terminal $\RealUp$ seal through $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-real-interval-chain-carrier}. The endpoint ledger $E$ and closed interval rows $I$ expose the finite interval cells before any containment or point-name request can be replayed.

The chain part is read through $J$ and $D$. The containment row $J$ keeps later cells inside earlier cells, while the $\DyadicRatCoreUp$ row $D$ records the diameter budget used by the finite precision request.

The Real-facing part is read only after the finite observation route has been displayed. The $\StreamNameUp$ windows $S$ determine the requested endpoint observations, the $\RegSeqRatUp$ row $R$ supplies regular rational readback, and the terminal $\RealUp$ seal $L$ is reached after those rows.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since no row carries host interval intersection, quotient-real equality, countable choice, open-cover compactness, detached completion data, or ambient completeness, the NameCert surface is exhausted by the displayed rows.
\end{proof}

\begin{closurestatus}{\FiniteRealIntervalChainUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-real-interval-chain-carrier} and \autoref{thm:finite-real-interval-chain-namecert-obligations} seed the finite interval-chain route from endpoint ledgers through closed interval cells, containment witnesses, dyadic budgets, StreamName windows, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, countable choice, quotient Real construction, selected host intersection point, detached completion object, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, interval-row exposure, containment witness transport, dyadic diameter budget exactness, readback route, Real seal non-escape, and TasteGate compatibility for BEDC.Derived.FiniteRealIntervalChainUp.}
  \constructivestory{A $\FiniteRealIntervalChainUp$ packet is generated from endpoint ledgers, closed interval rows, chain containment witnesses, DyadicRatCore diameter budgets, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and local NameCert rows.}
\end{closurestatus}
