\chapter{A Concrete Naming Certificate for $\RealEqualityReflectionUp$}
\label{ch:concrete-instances-real-equality-reflection-namecert}
\origin{human}

Following Bishop and Bridges' constructive analysis, equality of real numbers is presented through regular Cauchy data and explicit tolerance control rather than through an ambient quotient oracle. The $\RealEqualityReflectionUp$ packet names the finite equality-reflection boundary where the setoid route of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert} is exposed to the equality-facing consumers of \autoref{ch:concrete-instances-real-equality-namecert}. It records the route from regular rational streams and dyadic tolerance rows into the $\RealUp$ seal without adding selected representatives, quotient equality as a primitive, countable choice, host real extensionality, Lean verification, or bridge checking.

\begin{definition}[Real equality reflection carrier]
\label{def:real-equality-reflection-carrier}
A $\RealEqualityReflectionUp$ carrier is a finite $\BHist$ packet
$$
P=(Q,E,R,S,D,H,C,P_0,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\CauchyEquivalenceSetoidUp$ route that reads equality through finite Cauchy windows.
\item $E$ is the $\RealEqualityUp$ consumer row whose equality-facing request is admitted only after $Q$ is visible.
\item $R$ is the $\RegSeqRatUp$ regular rational source row used by the setoid route.
\item $S$ is the $\StreamNameUp$ window row opened before any equality consumer reads the source.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the visible windows and regular rational readback.
\item $H$ records componentwise $\hsame$ transport for the setoid route, equality consumer, source, windows, tolerance ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an equality-reflection request through $R,S,D,Q,E$ and then through the structural rows.
\item $P_0$ is the $\Pkg$ provenance over $\RealEqualityReflectionUp$, $\CauchyEquivalenceSetoidUp$, $\RealEqualityUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealEqualityReflectionUp}$ row.
\end{enumerate}
The carrier is admitted only when every $\RealEqualityUp$ read is downstream of the displayed $\CauchyEquivalenceSetoidUp$ route and every route into the $\RealUp$ seal still exposes the regular source, opened window, dyadic tolerance row, transport, replay, provenance, and local name.
\end{definition}

\begin{theorem}[Real equality reflection NameCert obligation surface]
\label{thm:real-equality-reflection-namecert-obligation-surface}
For every accepted $\RealEqualityReflectionUp$ carrier
$$
P=(Q,E,R,S,D,H,C,P_0,N),
$$
the local $\NameCert_{\RealEqualityReflectionUp}$ surface consists exactly of carrier admission, setoid-route exposure, real-classifier reflection, transport, replay, provenance, and non-escape rows. Carrier admission displays $Q,E,R,S,D,H,C,P_0,N$; setoid-route exposure requires $Q$ to read $\CauchyEquivalenceSetoidUp$ through $R,S,D$; real-classifier reflection requires the equality-facing consumer row $E$ to remain downstream of that setoid route before any $\RealUp$ seal is read; transport, replay, and provenance are carried only by $H,C,P_0$; non-escape is the assertion that no quotient-equality oracle, selected representative, countable-choice schedule, ambient real extensionality, Lean verification, or bridge coordinate is present.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-equality-reflection-carrier}. The projection exposes one setoid route, one equality-facing consumer row, one regular rational source, one opened window row, one dyadic tolerance ledger, and the structural transport, replay, provenance, and naming rows.

The setoid route is forced to pass through $R,S,D$ before the consumer row $E$ can read equality. Thus the packet first records the regular rational readback and finite StreamName inspection used by $\CauchyEquivalenceSetoidUp$.

The equality-facing row then reflects only that visible route into the Real boundary. Since the only structural rows are $H,C,P_0,N$, the packet can transport, replay, source, and name the displayed route but cannot add a quotient oracle, selected representative, choice schedule, ambient extensionality, Lean proof, or bridge datum.
\end{proof}

\begin{theorem}[Real equality reflection Cauchy setoid route]
\label{thm:real-equality-reflection-cauchy-setoid-route}
Every $\RealEqualityUp$ consumer exported by an accepted $\RealEqualityReflectionUp$ carrier factors through the finite route
$$
R,S,D\longmapsto Q\longmapsto E\longmapsto \RealUp .
$$
In particular, the consumer first reads the $\RegSeqRatUp$ source, the $\StreamNameUp$ finite window, and the $\DyadicRatCoreUp$ tolerance row, then exposes the $\CauchyEquivalenceSetoidUp$ route, and only after that may it reach the equality-facing $\RealUp$ seal.
\end{theorem}
\begin{proof}
Begin with an equality-facing request. Carrier admission gives the displayed rows $R,S,D,Q,E$ and no direct coordinate from the request to a Real seal.

Read $R,S,D$ first. These rows determine the regular source readback, finite window, and dyadic tolerance surface on which the Cauchy setoid comparison is visible.

Now read the setoid row $Q$ and only then the consumer row $E$. The target equality consumer therefore sees $\CauchyEquivalenceSetoidUp$ before $\RealEqualityUp$ reaches the $\RealUp$ seal, so the route has no hidden quotient equality, selected representative, countable choice, ambient completeness, Lean verification, or bridge checking coordinate.
\end{proof}

\falsifiablePrediction{A $\RealEqualityUp$ consumer that reaches a $\RealUp$ equality-facing seal from accepted $\RealEqualityReflectionUp$ data without first exposing the $\RegSeqRatUp$ source, $\StreamNameUp$ window, $\DyadicRatCoreUp$ tolerance row, and $\CauchyEquivalenceSetoidUp$ route refutes the carrier surface.}

\independenceWitness{cauchy-equivalence-setoid, real-equality, regseqrat, streamname, dyadicratcore, real: no listed sibling supplies the whole nine-row packet $P=(Q,E,R,S,D,H,C,P_0,N)$, because each sibling contributes only setoid, equality-consumer, source, window, tolerance, or seal data while this chapter binds them with transport, replay, provenance, and local naming.}

\begin{closurestatus}{\RealEqualityReflectionUp}
  \constructivestory{A $\RealEqualityReflectionUp$ packet is generated from a CauchyEquivalenceSetoid route, a RealEquality consumer row, a RegSeqRat source row, StreamName windows, a DyadicRatCore tolerance ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row before the Real seal is read.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-equality-reflection-carrier}, \autoref{thm:real-equality-reflection-namecert-obligation-surface}, and \autoref{thm:real-equality-reflection-cauchy-setoid-route} seed the finite equality-reflection surface over regular rational sources, finite windows, dyadic tolerances, Cauchy setoid routing, equality-facing consumers, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient equality as primitive, selected representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, setoid-route exposure, real-classifier reflection, transport, replay, provenance, and non-escape for BEDC.Derived.RealEqualityReflectionUp.}
\end{closurestatus}
