\chapter{A Concrete Naming Certificate for $\BrouwerFixedPointMetricUp$}
\label{ch:concrete-instances-brouwer-fixed-point-metric-namecert}
\origin{human}

Following Brouwer and constructive fixed-point treatments, the $\BrouwerFixedPointMetricUp$ packet records finite metric approximations to the fixed-point route on compact convex metric data. It consumes the compact finite-net discipline of \autoref{ch:concrete-instances-compactmetric-namecert} and the modulus-facing map discipline of \autoref{ch:concrete-instances-continuousmap-namecert}. The packet names mesh stages, approximate self-map witnesses, finite residual bounds, transport, replay, provenance, and local naming; it does not assert an unrestricted classical Brouwer fixed-point theorem.

\begin{definition}[Brouwer fixed-point metric carrier]
\label{def:brouwer-fixed-point-metric-carrier}
A $\BrouwerFixedPointMetricUp$ carrier is a finite $\BHist$ packet
$$
F=(K,X,M,G,E,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact metric source row, read through the finite-cover and finite-net surface of $\CompactMetricUp$.
\item $X$ is the convex-cell ledger naming the finite simplex or box cells inspected at the current mesh scale.
\item $M$ is the $\ContinuousMapUp$ row for the self-map whose finite modulus is being used.
\item $G$ is the mesh-stage ledger, recording the finite grid, adjacency, and boundary-face rows inspected at that stage.
\item $E$ is the approximate fixed-point evidence row, recording a cell, mesh point, or finite witness whose residual is bounded at the displayed tolerance.
\item $R$ is the residual-bound row, comparing the map value and witness through metric radii available from $K,M,G$.
\item $H$ records componentwise $\hsame$ transport for compact metric data, convex-cell rows, continuous-map rows, mesh stages, evidence rows, residual rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay for the finite route
$$
K,X,M,G \longmapsto E,R .
$$
\item $P$ is the $\Pkg$ provenance over $\BrouwerFixedPointMetricUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\MetricSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BrouwerFixedPointMetricUp}$ row.
\end{enumerate}
The carrier has no coordinate for a host-selected exact fixed point, unrestricted compactness, quotient equality of completions, countable choice, or a global real-valued existence theorem.
\end{definition}

\begin{theorem}[Brouwer fixed-point metric NameCert obligations]
\label{thm:brouwer-fixed-point-metric-namecert-obligations}
For an accepted $\BrouwerFixedPointMetricUp$ carrier
$$
F=(K,X,M,G,E,R,H,C,P,N),
$$
the local $\NameCert_{\BrouwerFixedPointMetricUp}$ surface consists exactly of compact metric admission through $K$, convex-cell exposure through $X$, continuous-map modulus access through $M$, finite mesh-stage discipline through $G$, approximate witness exposure through $E$, residual-bound readback through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:brouwer-fixed-point-metric-carrier}. The accepted packet exposes only compact metric data, convex-cell data, a continuous self-map row, finite mesh-stage rows, approximate witness rows, residual-bound rows, and the structural rows $H,C,P,N$.

The compact and map faces are read through $K$ and $M$. The compact metric row supplies only finite-net and radius information, while the continuous-map row supplies only the displayed finite modulus data needed by the mesh stage.

The approximation face is read through $G,E,R$. The mesh row names the finite grid and boundary checks, the evidence row names the finite approximate witness, and the residual row records the metric comparison available at that tolerance.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since no exact host fixed point or unrestricted choice principle appears among the rows, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Brouwer fixed-point metric finite-approximation non-escape]
\label{thm:brouwer-fixed-point-metric-finite-approximation-nonescape}
Every consumer read of an accepted $\BrouwerFixedPointMetricUp$ packet factors through the finite approximation route
$$
K,X,M,G \longmapsto E,R \longmapsto H,C,P,N .
$$
The consumer may read compact finite-net data, convex-cell rows, continuous-map modulus data, finite mesh stages, approximate witness rows, residual bounds, transport, replay, provenance, and local naming. It cannot read an unrestricted exact fixed point, a host compactness oracle, quotient-completion equality, countable choice, or an ambient $\RealUp$ completeness principle from the packet.
\end{theorem}
\begin{proof}
Start with \autoref{def:brouwer-fixed-point-metric-carrier}. The only route from compact metric and continuous-map data to a fixed-point-facing conclusion is the displayed finite mesh route through $K,X,M,G,E,R$.

Apply \autoref{thm:brouwer-fixed-point-metric-namecert-obligations}. The local NameCert forces every consumer to inspect compact metric admission, convex-cell exposure, continuous-map access, and mesh-stage discipline before the approximate witness or residual bound can be read.

Transport and replay do not add a stronger theorem. The rows $H$ and $C$ preserve the same finite approximation route, while $P$ and $N$ record provenance and local naming. Hence the packet exports finite approximate fixed-point evidence only, not the classical unrestricted Brouwer assertion.
\end{proof}

\closureat{BrouwerFixedPointMetricUp}{seedStr}

\begin{closurestatus}{\BrouwerFixedPointMetricUp}
  \constructivestory{A $\BrouwerFixedPointMetricUp$ packet is generated from compact metric rows, convex-cell rows, continuous self-map modulus rows, finite mesh-stage rows, approximate witness rows, residual-bound rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:brouwer-fixed-point-metric-carrier}, \autoref{thm:brouwer-fixed-point-metric-namecert-obligations}, and \autoref{thm:brouwer-fixed-point-metric-finite-approximation-nonescape} seed the finite metric approximation packet for Brouwer-style fixed-point consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close an unrestricted exact Brouwer fixed-point theorem, countable choice, host compactness, quotient-completion equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact metric routing, continuous-map modulus routing, mesh-stage discipline, approximate witness exposure, residual-bound readback, transport stability, replay stability, provenance, and local naming for BEDC.Derived.BrouwerFixedPointMetricUp.}
\end{closurestatus}
