\chapter{A Concrete Naming Certificate for $\MetaCICGroundCompilerNormalizationRouteUp$}
\label{ch:concrete-instances-metacic-ground-compiler-normalization-route-namecert}
\origin{ai}

The $\MetaCICGroundCompilerNormalizationRouteUp$ packet realizes the normalization audit map as finite ground-compiler data. It consumes the critical-path reading of \autoref{ch:concrete-instances-metaciccriticalpath-namecert} and the candidate-mediated normalization interface recorded in \autoref{ch:metacic-normalization-audit-map}. The packet names generated closed terms, candidate evidence, candidate-set membership, no-infinite-reduction readback, compiler replay, obstruction boundary rows, transport, provenance, and local naming without turning candidate evidence into an unconditional global normalization oracle.

\begin{definition}[MetaCIC ground-compiler normalization route carrier]
\label{def:metacic-ground-compiler-normalization-route-carrier}
A $\MetaCICGroundCompilerNormalizationRouteUp$ carrier is a finite $\BHist$ packet
$$
G=(T,A,S,Q,N,R,O,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the generated closed-term row emitted by the ground compiler.
\item $A$ is the typing and closedness audit row for the generated term.
\item $S$ is the candidate-evidence row, recording the reducibility candidate, closed candidate, or candidate-set membership route consumed by the normalization proof.
\item $Q$ is the Pi/application adequacy row that keeps the candidate evidence stable across the inspected compiler route.
\item $N$ is the strong-normalization readback row obtained from the candidate evidence.
\item $R$ is the no-infinite-reduction readback row obtained from the same evidence.
\item $O$ is the obstruction-boundary row recording that no unconditional closed-term normalization theorem is being claimed.
\item $H$ records componentwise $\hsame$ transport for generated terms, audit rows, candidate rows, adequacy rows, normalization readback, no-infinite-reduction readback, obstruction rows, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay for the finite route
$$
T,A,S,Q \longmapsto N,R,O .
$$
\item $P$ is the $\Pkg$ provenance over $\MetaCICGroundCompilerNormalizationRouteUp$, $\MetaCICCriticalPathUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $L$ is the local $\NameCert_{\MetaCICGroundCompilerNormalizationRouteUp}$ row.
\end{enumerate}
The carrier has no coordinate for unconditional normalization of all closed MetaCIC terms, subject-reduction closure, confluence closure, hidden compiler trust, or host-level termination.
\end{definition}

\begin{theorem}[MetaCIC ground-compiler normalization route NameCert obligations]
\label{thm:metacic-ground-compiler-normalization-route-namecert-obligations}
For an accepted $\MetaCICGroundCompilerNormalizationRouteUp$ carrier
$$
G=(T,A,S,Q,N,R,O,H,C,P,L),
$$
the local $\NameCert_{\MetaCICGroundCompilerNormalizationRouteUp}$ surface consists exactly of generated closed-term admission through $T$, typing and closedness audit through $A$, candidate-evidence exposure through $S$, Pi/application adequacy routing through $Q$, strong-normalization readback through $N$, no-infinite-reduction readback through $R$, obstruction-boundary recording through $O$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $L$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:metacic-ground-compiler-normalization-route-carrier}. The accepted packet exposes generated term data, typing and closedness audit data, candidate evidence, adequacy routing, normalization readback, no-infinite-reduction readback, obstruction boundary, and the structural rows $H,C,P,L$.

The normalization face is read through $S,Q,N,R$. Candidate evidence is displayed before any strong-normalization or no-infinite-reduction conclusion is consumed, and the adequacy row records the Pi/application routing needed by the compiler path.

The boundary row $O$ is part of the same packet. It records that the route is evidence-bearing and does not erase the candidate input into a blanket theorem for every closed term.

Finally $H,C,P,L$ transport, replay, source, and name exactly this route. Since the carrier has no coordinate for subject-reduction closure, confluence closure, hidden compiler trust, or host termination, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[MetaCIC ground-compiler candidate non-escape]
\label{thm:metacic-ground-compiler-normalization-route-candidate-nonescape}
Every normalization-facing consumer read of an accepted $\MetaCICGroundCompilerNormalizationRouteUp$ packet factors through the finite route
$$
T,A,S,Q \longmapsto N,R,O \longmapsto H,C,P,L .
$$
Thus strong-normalization and no-infinite-reduction readbacks remain tied to generated closed-term audit rows, candidate evidence, and Pi/application adequacy rows. The packet cannot export unconditional normalization for all closed MetaCIC terms, subject-reduction closure, confluence closure, hidden compiler trust, or host-level termination.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:metacic-ground-compiler-normalization-route-carrier}. The rows $N$ and $R$ occur only after the generated term audit $T,A$ and the candidate route $S,Q$ have been displayed.

Apply \autoref{thm:metacic-ground-compiler-normalization-route-namecert-obligations}. It forces every normalization-facing read to expose the generated closed term, its typing and closedness audit, the candidate evidence, and the adequacy route before reading normalization or no-infinite-reduction consequences.

The obstruction row $O$ keeps the boundary visible, and the rows $H,C,P,L$ only transport, replay, source, and name the same packet. Therefore the consumer cannot detach $N$ or $R$ from candidate evidence or promote the route to a global MetaCIC normalization theorem.
\end{proof}

\closureat{MetaCICGroundCompilerNormalizationRouteUp}{seedStr}

\begin{closurestatus}{\MetaCICGroundCompilerNormalizationRouteUp}
  \constructivestory{A $\MetaCICGroundCompilerNormalizationRouteUp$ packet is generated from ground-compiler closed-term rows, typing and closedness audit rows, candidate-evidence rows, Pi/application adequacy rows, normalization readback rows, no-infinite-reduction rows, obstruction-boundary rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:metacic-ground-compiler-normalization-route-carrier}, \autoref{thm:metacic-ground-compiler-normalization-route-namecert-obligations}, and \autoref{thm:metacic-ground-compiler-normalization-route-candidate-nonescape} seed the finite ground-compiler normalization route over candidate evidence.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close unconditional normalization for all closed MetaCIC terms, subject reduction, confluence, hidden compiler trust, host termination, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked generated-term admission, typing and closedness audit, candidate-evidence routing, Pi/application adequacy routing, strong-normalization readback, no-infinite-reduction readback, obstruction-boundary recording, transport stability, replay stability, provenance, and local naming for BEDC.Derived.MetaCICGroundCompilerNormalizationRouteUp.}
\end{closurestatus}
