\chapter{A Concrete Naming Certificate for $\GammaConvergenceUp$}
\label{ch:concrete-instances-gamma-convergence-namecert}
\origin{human}

Following Dal Maso on Gamma-convergence, the $\GammaConvergenceUp$ packet records the finite variational-convergence surface by which lower-bound and recovery-window data are routed to compactness and real-valued consumers. It sits after the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the compact finite-read discipline of \autoref{ch:concrete-instances-compactmetric-namecert}, the lower-semicontinuity boundary of \autoref{ch:concrete-instances-lowersemicontinuous-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only displayed liminf ledgers, recovery windows, compactness windows, real-value readbacks, transport, replay, provenance, and local naming; it does not assert host minimizer existence, quotient equality of functionals, selected recovery sequences, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[Gamma-convergence carrier]
\label{def:gamma-convergence-carrier}
A $\GammaConvergenceUp$ carrier is a finite $\BHist$ packet
$$
G=(X,K,L,F,A,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\MetricUp$ source row on which the variational data are inspected.
\item $K$ is the $\CompactMetricUp$ finite compactness-window row used by subsequence-facing consumers.
\item $L$ is the $\LowerSemicontinuousUp$ liminf-boundary row for the inspected functionals.
\item $F$ is the finite functional-index and value-window ledger.
\item $A$ is the liminf-test row, recording every displayed approach window and its lower-bound comparison.
\item $R$ is the recovery-window row, recording finite witnesses that a downstream consumer may replay without selecting a host recovery sequence.
\item $Q$ is the $\RegSeqRatUp$ readback row for rational value windows exposed by $A$ and $R$.
\item $E$ is the terminal $\RealUp$ seal row reached only after $X,K,L,F,A,R,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the displayed rows.
\item $C$ records displayed $\Cont$ replay from metric and compact windows to the lower-bound, recovery, readback, and seal rows.
\item $P$ is the $\Pkg$ provenance over $\GammaConvergenceUp$, $\MetricUp$, $\CompactMetricUp$, $\LowerSemicontinuousUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\GammaConvergenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,K,L,F,A,R,Q,E,H,C,P,N$. It has no coordinate for quotient equality of functionals, selected minimizers, selected recovery sequences, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Gamma-convergence NameCert obligations]
\label{thm:gamma-convergence-namecert-obligations}
For an accepted $\GammaConvergenceUp$ carrier $G=(X,K,L,F,A,R,Q,E,H,C,P,N)$, the local $\NameCert_{\GammaConvergenceUp}$ surface consists exactly of carrier admission, metric-source exposure through $X$, compact finite-window exposure through $K$, lower-semicontinuity exposure through $L$, finite functional-window exposure through $F$, liminf-test exposure through $A$, recovery-window exposure through $R$, regular rational readback through $Q$, terminal real sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.

Every variational consumer of the packet must therefore read the finite route
$$
\MetricUp,\ \CompactMetricUp,\ \LowerSemicontinuousUp,\ \RegSeqRatUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert
$$
before it may inspect a Gamma-limit-facing value. The exported route is a finite NameCert boundary for liminf and recovery data, not a host compactness theorem, a selected minimizer, quotient equality of functionals, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:gamma-convergence-carrier}. The rows $X,K,L,F,A,R,Q,E$ are the only coordinates from which a variational consumer may read metric source data, compact windows, lower-semicontinuity tests, finite functional windows, liminf checks, recovery windows, rational readbacks, and terminal real seals.

The liminf side is generated by $A$ only after $X,K,L,F$ have been displayed. Thus a lower-bound read cannot bypass the metric row, compact finite-window row, lower-semicontinuity row, or finite value-window ledger.

The recovery side is generated by $R$ and read back through $Q$ before $E$ is visible. Since $H,C,P,N$ preserve only the displayed rows under transport, replay, provenance, and local naming, they cannot add a selected recovery sequence, a minimizer, quotient equality, or an ambient completeness theorem.

Consequently the local NameCert obligations are exhausted by the listed finite rows. Any stronger variational principle must be supplied by a later consumer, not by the $\GammaConvergenceUp$ packet itself.
\end{proof}

\falsifiablePrediction{Every accepted $\GammaConvergenceUp$ consumer that reaches a Real-facing Gamma-limit value without first reading a Metric row, CompactMetric row, LowerSemicontinuous row, liminf-test row, recovery-window row, RegSeqRat readback row, transport, replay, provenance, and local NameCert row refutes the carrier surface.}

\independenceWitness{metric, compactmetric, lowersemicontinuous, regseqrat, real, mosco-convergence: $\GammaConvergenceUp$ is not bijective to any listed sibling because the packet jointly stores liminf tests, recovery windows, compact finite-read boundaries, rational value readbacks, terminal real seals, transport, replay, provenance, and local naming.}

\closureat{GammaConvergenceUp}{seedStr}

\begin{closurestatus}{\GammaConvergenceUp}
  \theoryclosure{\seedClosure}
  \constructivestory{A $\GammaConvergenceUp$ packet is generated from a metric source row, compact finite-window row, lower-semicontinuity row, finite functional windows, liminf-test rows, recovery-window rows, RegSeqRat readback, a RealUp seal, componentwise transport, continuation replay, provenance, and a local NameCert row.}
  \scopeclosed{\autoref{def:gamma-convergence-carrier} and \autoref{thm:gamma-convergence-namecert-obligations} seed the finite variational-convergence certificate over Metric, CompactMetric, LowerSemicontinuous, RegSeqRat, Real, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, host minimizer existence, selected recovery sequences, quotient equality of functionals, countable choice, open-cover compactness, or ambient $\RealUp$ completeness.}
  \upgradepath{Formalization requires a BEDC.Derived.GammaConvergenceUp carrier together with checked liminf, recovery-window, compactness-window, readback, transport, provenance, and local naming obligations.}
\end{closurestatus}
