\chapter{A Concrete Naming Certificate for $\ConstructivePolishSpaceUp$}
\label{ch:concrete-instances-constructive-polish-space-namecert}
\origin{human}

Following Bishop and Bridges on complete separable metric spaces in constructive analysis, the $\ConstructivePolishSpaceUp$ packet records the L10 completion frontier as finite NameCert data. It sits after the completion source of \autoref{ch:concrete-instances-metriccompletion-namecert}, the separated classifier of \autoref{ch:concrete-instances-separatedmetric-namecert}, the finite observation schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real seal of \autoref{ch:concrete-instances-real-namecert}, the effective separable surface of \autoref{ch:concrete-instances-effective-polish-space-namecert}, and the compact subcase of \autoref{ch:concrete-instances-compact-polish-space-namecert}. The packet names a completion-facing constructive Polish carrier without claiming quotient completions, countable choice, host point equality, or ambient $\RealUp$ completeness.

\begin{definition}[ConstructivePolishSpace carrier]\label{def:constructive-polish-space-carrier}
A $\ConstructivePolishSpaceUp$ carrier is a finite $\BHist$ packet
$$
P=(M,S,D,W,Q,R,L,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricCompletionUp$ source row, exposing only the completion request, finite tolerance ledger, and completion-facing handoff consumed by the packet.
\item $S$ is the $\SeparatedMetricUp$ classifier row, requiring zero-distance agreement for displayed points to pass through the separated metric boundary.
\item $D$ is the dense-sequence row. It names the finite prefix and readback schedule inspected by a completion consumer, not an infinite choice of representatives.
\item $W$ is the $\StreamNameUp$ finite-window row for dense-name observations, Cauchy windows, and requested precision budgets.
\item $Q$ is the $\RegSeqRatUp$ readback row for regular rational approximants, tolerance comparisons, and Cauchy witness reads.
\item $R$ is the $\RealUp$ seal row, exposed only after the finite stream windows and regular rational readbacks have been displayed.
\item $L$ is the located completion service row, answering each displayed approximation request through $M,S,D,W,Q,R$.
\item $H$ records componentwise $\hsame$ transport for the metric-completion source, separated classifier, dense schedule, stream windows, regular rational readback, Real seal, located service, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a finite completion request through $W,Q,R$ and then back to $M,S,D,L$.
\item $G$ is the $\Pkg$ provenance over $\ConstructivePolishSpaceUp$, $\MetricCompletionUp$, $\SeparatedMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\EffectivePolishSpaceUp$, $\CompactPolishSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\ConstructivePolishSpaceUp}$ row.
\end{enumerate}
The carrier exports only this displayed finite completion route. It has no coordinate for quotient completion classes, countable choice over dense points, host point equality, selected representatives, or an unrestricted completeness principle for $\RealUp$.
\end{definition}

\begin{theorem}[ConstructivePolishSpace NameCert obligation surface]\label{thm:constructive-polish-space-namecert-obligation-surface}
For every accepted $\ConstructivePolishSpaceUp$ carrier $P=(M,S,D,W,Q,R,L,H,C,G,N)$, the local $\NameCert_{\ConstructivePolishSpaceUp}$ surface consists exactly of carrier admission, separated zero-distance classification, dense-prefix readback, finite StreamName window admission, RegSeqRat regular readback, Real seal handoff, located completion service replay, componentwise transport, provenance, and local naming through the displayed rows $M,S,D,W,Q,R,L,H,C,G,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:constructive-polish-space-carrier}. The tuple displays exactly the metric-completion source, separated classifier, dense schedule, StreamName windows, RegSeqRat readback, Real seal, located completion service, transport, replay, provenance, and local naming rows.

A completion-facing request must first choose a finite window in $W$ and a finite dense-prefix read through $D$. The regular rational row $Q$ turns those observations into tolerance data before the terminal Real seal $R$ can be inspected.

The separated classifier $S$ is the only row that compares displayed points, and it does so over the completion source $M$. The located service $L$, transport row $H$, replay row $C$, provenance row $G$, and local name row $N$ package this same route, so no excluded quotient, choice, host-equality, or ambient-completeness coordinate is available.
\end{proof}

\begin{theorem}[ConstructivePolishSpace completion readback route]\label{thm:constructive-polish-space-completion-readback-route}
Every completion-facing read served by an accepted $\ConstructivePolishSpaceUp$ packet factors through the finite route
$$
D,W \longmapsto Q \longmapsto R \longmapsto M,S,L \longmapsto H,C,G,N .
$$
Thus an $\EffectivePolishSpaceUp$ or $\CompactPolishSpaceUp$ consumer may read dense schedules, finite windows, regular rational approximants, the terminal Real seal, and the located completion service, but it cannot extract quotient completion equality, a countable-choice selector, host point equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a completion-facing consumer. The only dense-name data in the packet is $D$, and the only observation schedule is $W$, so the consumer first receives a finite dense prefix and finite stream windows.

The readback then passes through $Q$ and $R$. This exposes regular rational approximants and a Real seal only after the finite observations have been displayed.

Finally the route returns to the completion source $M$, separated classifier $S$, and located service $L$, then through the structural rows $H,C,G,N$. Since no other coordinate appears in the carrier, the listed quotient, choice, host-equality, and ambient-completeness claims cannot be read from the packet.
\end{proof}

\closureat{ConstructivePolishSpaceUp}{seedStr}

\begin{closurestatus}{\ConstructivePolishSpaceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:constructive-polish-space-carrier}, \autoref{thm:constructive-polish-space-namecert-obligation-surface}, and \autoref{thm:constructive-polish-space-completion-readback-route} seed the finite constructive Polish completion route over metric completion, separated classification, dense schedules, StreamName windows, RegSeqRat readback, Real sealing, located completion service, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, quotient completion equality, countable choice, host point equality, selected representatives, standard bridge checking, or ambient RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-prefix readback, separated classifier stability, completion-readback routing, nonescape, and local naming for BEDC.Derived.ConstructivePolishSpaceUp.}
  \constructivestory{A $\ConstructivePolishSpaceUp$ packet is generated from a MetricCompletion source row, a SeparatedMetric classifier row, finite dense schedules, StreamName windows, RegSeqRat readback, a RealUp seal, located completion service, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
