\chapter{A Concrete Naming Certificate for $\ConstructiveSobolevEnergyUp$}
\label{ch:concrete-instances-constructive-sobolev-energy-namecert}
\origin{human}

Following Sobolev and Bishop--Bridges constructive analysis, the $\ConstructiveSobolevEnergyUp$ packet records finite energy evidence for a displayed function row and its weak-derivative rows without passing through a host quotient space. It sits after the Sobolev comparison surface of \autoref{ch:concrete-instances-sobolev-namecert}, the Sobolev-space carrier of \autoref{ch:concrete-instances-sobolev-space-namecert}, the Hilbert inner-product route of \autoref{ch:concrete-instances-hilbert-namecert}, and the terminal real readback seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives PDE, trace, and embedding consumers a finite energy certificate surface rather than a completed function space.

\begin{definition}[Constructive Sobolev energy carrier]
\label{def:constructive-sobolev-energy-carrier}
A $\ConstructiveSobolevEnergyUp$ carrier is a finite $\BHist$ packet
$$
S=(F,D,E,A,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the function row. It records the visible domain name, target $\RealUp$ readback route, finite test-window requests, and the stream or regular-rational windows through which function values are inspected.
\item $D$ is the weak-derivative row. It records the finite multi-index list, test-window signs, integration-by-parts witnesses, and derivative readback windows imported from the weak-derivative and Sobolev siblings.
\item $E$ is the energy norm row. It records the displayed $L^2$-style summands, Hilbert inner-product requests, rational upper bounds, and real seal endpoints used to certify finite energy.
\item $A$ is the dyadic approximation row. It records finite dyadic tolerances, local mesh windows, rational error bounds, and replayable approximation requests for $F,D,E$.
\item $B$ is the boundary and trace row. It records only the trace windows, boundary test rows, and compatibility checks explicitly present in the packet.
\item $H$ records componentwise $\hsame$ transport across $F,D,E,A,B$.
\item $C$ records displayed $\Cont$ replay from a Sobolev-energy request through the function row, weak-derivative rows, energy norm row, dyadic approximation row, boundary and trace row, and transport row.
\item $P$ is the $\Pkg$ provenance row over $\ConstructiveSobolevEnergyUp$, $\SobolevUp$, $\SobolevSpaceUp$, $\HilbertUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ConstructiveSobolevEnergyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. No coordinate stores a host quotient of functions, a measure-completed representative class, a Hahn--Banach separator, an open-cover compactness theorem, a selected trace representative, countable choice, or ambient equality of functions.
\end{definition}

\begin{closurestatus}{\ConstructiveSobolevEnergyUp}
  \constructivestory{A $\ConstructiveSobolevEnergyUp$ packet is generated from a function row, weak-derivative rows, an energy norm row, dyadic approximation data, boundary and trace data, componentwise transport, continuation replay, provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:constructive-sobolev-energy-carrier} binds the finite carrier surface for Sobolev energy certificates over displayed function, derivative, approximation, boundary, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host function quotients, measure-completion claims, Hahn--Banach separation, open-cover compactness, choice, or bridge checking.}
  \upgradepath{Obligation closure requires checking carrier admission, energy-row exactness, derivative-row replay, trace-window non-escape, and local NameCert stability for the displayed packet.}
\end{closurestatus}
