\chapter{A Concrete Naming Certificate for $\CauchyCompletionReflectorTriangleHandoffUp$}
\label{ch:concrete-instances-cauchy-completion-reflector-triangle-handoff-namecert}
\origin{human}

Following Bishop--Bridges constructive completion and Mac Lane's adjunction language, the $\CauchyCompletionReflectorTriangleHandoffUp$ packet records the finite handoff by which the Cauchy completion reflector and its triangle identities become a local L10 NameCert surface. It sits over the reflector of \autoref{ch:concrete-instances-cauchycompletionreflector-namecert}, the triangle packet of \autoref{ch:concrete-instances-completion-reflector-triangle-namecert}, the unit of \autoref{ch:concrete-instances-cauchycompletionunit-namecert}, the counit of \autoref{ch:concrete-instances-cauchy-completion-counit-namecert}, the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the finite coherence route; it does not assert quotient completion, selected representatives, countable choice, host equality, or ambient $\RealUp$ completeness.

\begin{definition}[CauchyCompletionReflectorTriangleHandoff carrier]
\label{def:cauchy-completion-reflector-triangle-handoff-carrier}
A $\CauchyCompletionReflectorTriangleHandoffUp$ carrier is a finite $\BHist$ packet
$$
H=(F,T,U,K,S,D,R,E,J,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyCompletionReflectorUp$ row exposing the reflector as a finite completion-facing surface.
\item $T$ is the $\CompletionReflectorTriangleUp$ row binding the unit, counit, and idempotent triangle around the same reflector.
\item $U$ is the $\CauchyCompletionUnitUp$ row for source admission into the completion-facing route.
\item $K$ is the $\CauchyCompletionCounitUp$ row for already completed or real-sealed return reads.
\item $S$ is the $\StreamNameUp$ finite-window row through which source and completed names are observed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used by the same windows before any real seal is read.
\item $R$ is the $\RegSeqRatUp$ regular readback row carried from source names to completion-facing reads.
\item $E$ is the terminal $\RealUp$ seal row available only after the window, tolerance, and regular readback rows are displayed.
\item $J$ records componentwise $\hsame$ transport for reflector, triangle, unit, counit, window, tolerance, readback, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay along
$$
F,T,U,K \longmapsto S,D,R,E \longmapsto J,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyCompletionReflectorTriangleHandoffUp$, $\CauchyCompletionReflectorUp$, $\CompletionReflectorTriangleUp$, $\CauchyCompletionUnitUp$, $\CauchyCompletionCounitUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CauchyCompletionReflectorTriangleHandoffUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these displayed rows. It has no coordinate for quotient completion, a selected representative, a countable-choice schedule, host equality, or ambient real completeness.
\end{definition}

\begin{theorem}[CauchyCompletionReflectorTriangleHandoff NameCert obligations]
\label{thm:cauchy-completion-reflector-triangle-handoff-namecert-obligations}
For every accepted $\CauchyCompletionReflectorTriangleHandoffUp$ carrier $H=(F,T,U,K,S,D,R,E,J,C,P,N)$, the local $\NameCert_{\CauchyCompletionReflectorTriangleHandoffUp}$ surface consists exactly of carrier admission for the displayed reflector, triangle, unit, counit, stream window, dyadic tolerance, regular readback, real seal, transport, replay, provenance, and local naming rows; reflector exposure through $F$ before triangle reads through $T$; triangle coherence through the shared $U,K$ unit-counit boundary; regular-Cauchy handoff through $S,D,R,E$; transport and replay stability through $J,C$; and non-escape from quotient completion, selected representatives, countable choice, host equality, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-completion-reflector-triangle-handoff-carrier}. The rows $F,T,U,K,S,D,R,E,J,C,P,N$ are exactly the finite data admitted by the local packet.

The reflector is exposed first by $F$, and the triangle row $T$ may be read only as the unit-counit-idempotent surface attached to that reflector. The unit row $U$ and counit row $K$ therefore share the same completion-facing boundary.

The regular-Cauchy part is forced through $S,D,R,E$. Finite StreamName windows, dyadic tolerance data, and RegSeqRat readback are displayed before the terminal Real seal can be consumed.

Finally $J,C,P,N$ transport, replay, source, and name the same route. Since no carrier coordinate stores quotient completion, a selected representative, countable choice, host equality, or ambient real completeness, the listed obligations exhaust the accepted NameCert surface.
\end{proof}

\begin{theorem}[CauchyCompletionReflectorTriangleHandoff nonescape]
\label{thm:cauchy-completion-reflector-triangle-handoff-nonescape}
Every accepted $\CauchyCompletionReflectorTriangleHandoffUp$ packet exports the reflector-triangle handoff only through
$$
\CauchyCompletionReflectorUp,\ \CompletionReflectorTriangleUp,\ \CauchyCompletionUnitUp,\ \CauchyCompletionCounitUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
It exports no quotient completion, selected representative, countable-choice selector, host equality, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchy-completion-reflector-triangle-handoff-namecert-obligations}. It requires every accepted handoff to expose $F,T,U,K,S,D,R,E$ before the structural rows are consumed.

The reflector and triangle siblings supply only displayed L10 completion rows, and the Real-facing path is confined to finite stream windows, dyadic tolerance, regular readback, and a terminal Real seal. None of those rows is a quotient carrier or a selected representative.

The structural rows $J,C,P,N$ preserve and name the same finite route. The forbidden host-side and choice-side principles have no carrier coordinate, so they cannot be exported by an accepted packet.
\end{proof}

\closureat{CauchyCompletionReflectorTriangleHandoffUp}{seedStr}

\begin{closurestatus}{\CauchyCompletionReflectorTriangleHandoffUp}
  \constructivestory{A $\CauchyCompletionReflectorTriangleHandoffUp$ packet is generated from reflector, triangle, unit, counit, stream-window, dyadic-tolerance, regular-readback, Real-seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-completion-reflector-triangle-handoff-carrier}, \autoref{thm:cauchy-completion-reflector-triangle-handoff-namecert-obligations}, and \autoref{thm:cauchy-completion-reflector-triangle-handoff-nonescape} seed the finite completion-reflector triangle handoff surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, reflector exposure, triangle-unit-counit coherence, regular-Cauchy handoff, transport and replay stability, provenance, local naming, and non-escape for BEDC.Derived.CauchyCompletionReflectorTriangleHandoffUp.}
\end{closurestatus}
