\chapter{A Concrete Naming Certificate for $\AlmostPeriodicUp$}
\label{ch:concrete-instances-almost-periodic-namecert}
\origin{human}

Following Bohr and Besicovitch on almost periodic functions, read through Bishop--Bridges constructive analysis, the $\AlmostPeriodicUp$ packet records relative-density translation data for displayed real-valued function windows as finite BEDC rows. It sits beside the compact-source sup-norm ledger of \autoref{ch:concrete-instances-continuous-sup-norm-namecert}, the modulus-composition route of \autoref{ch:concrete-instances-uniform-modulus-composition-namecert}, the Dini finite-window route of \autoref{ch:concrete-instances-dini-uniform-monotone-namecert}, the compact-uniform-continuity packet of \autoref{ch:concrete-instances-compactuniformcontinuity-namecert}, and the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}. The packet names only finite translation ledgers and displayed sup-norm comparisons; it does not assert host function equality, an infinite hull compactification, Bohr compactification, quotient function-space equality, open-cover compactness, or ambient $\RealUp$ completeness.

\begin{definition}[AlmostPeriodic carrier]
\label{def:almost-periodic-carrier}
An $\AlmostPeriodicUp$ carrier is a finite $\BHist$ packet
$$
A=(F,T,N_{\mathrm{rel}},S,M,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the function-window row, listing the finite source windows and $\RealUp$-valued observations of the displayed function.
\item $T$ is the translation-budget row, naming the finite translation requests, tolerance budgets, and admissible translated windows.
\item $N_{\mathrm{rel}}$ is the relatively-dense finite-net row, recording the bounded search interval and the finite list of candidate translations exposed to a consumer.
\item $S$ is the sup-norm comparison row, read through the $\ContinuousSupNormUp$ surface and comparing each translated window only by displayed Real-sealed bounds.
\item $M$ is the uniform-modulus row, assembled through $\UniformModulusCompositionUp$ and the compact-uniform-continuity route before any translated read reaches $S$.
\item $U$ is the Dini and compact-uniform handoff row, recording the finite monotone-window and compact-continuity evidence consumed from $\DiniUniformMonotoneUp$ and $\CompactUniformContinuityUp$.
\item $H$ records componentwise $\hsame$ transport for function windows, translation budgets, relatively-dense nets, sup-norm comparisons, uniform moduli, sibling handoffs, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a tolerance request through $F,T,N_{\mathrm{rel}},S,M,U,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\AlmostPeriodicUp$, $\ContinuousSupNormUp$, $\UniformModulusCompositionUp$, $\DiniUniformMonotoneUp$, $\CompactUniformContinuityUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AlmostPeriodicUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,T,N_{\mathrm{rel}},S,M,U,H,C,P,N$. It has no coordinate for host-level equality of functions, an infinite translation hull, quotient function spaces, choice-selected periods, open-cover compactness, or ambient Real completeness.
\end{definition}

\begin{theorem}[AlmostPeriodic NameCert obligations]
\label{thm:almost-periodic-namecert-obligations}
For every accepted $\AlmostPeriodicUp$ carrier $A=(F,T,N_{\mathrm{rel}},S,M,U,H,C,P,N)$, the local $\NameCert_{\AlmostPeriodicUp}$ surface consists exactly of function-window admission, translation-budget accounting, relatively-dense finite-net exposure, sup-norm comparison through displayed Real-sealed bounds, uniform-modulus routing, Dini and compact-uniform sibling handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:almost-periodic-carrier}. The function rows, translation rows, relatively-dense net, sup-norm comparison, uniform-modulus handoff, and sibling rows are the only mathematical coordinates before transport, replay, provenance, and naming.

The translation read is finite. A tolerance request first enters $T$, then opens only the candidates listed in $N_{\mathrm{rel}}$, and then compares translated windows through $S$.

The comparison is real-facing but not host-functional. The row $S$ reads $\ContinuousSupNormUp$ and terminal $\RealUp$ seals, while $M$ and $U$ route modulus evidence through \autoref{ch:concrete-instances-uniform-modulus-composition-namecert}, \autoref{ch:concrete-instances-dini-uniform-monotone-namecert}, and \autoref{ch:concrete-instances-compactuniformcontinuity-namecert}.

Rows $H,C,P,N$ transport, replay, source, and name exactly the same finite route. Since no excluded hull, quotient, host equality, choice-selected period, compactness, or completeness coordinate appears in the carrier, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[AlmostPeriodic sup-norm translation stability]
\label{thm:almost-periodic-supnorm-translation-stability}
Every accepted $\AlmostPeriodicUp$ packet exposes a translation-stability read only through the finite route
$$
F,T,N_{\mathrm{rel}} \longrightarrow M,U \longrightarrow S \longrightarrow H,C,P,N .
$$
Thus a consumer may read a translated function window, a displayed translation budget, a relatively-dense finite-net candidate, a uniform-modulus handoff, and a sup-norm comparison row, but it may not replace this route by host equality of functions, an infinite period hull, quotient function-space equality, a choice-selected translation, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from the accepted carrier. Rows $F,T,N_{\mathrm{rel}}$ determine which function windows and translation candidates can be inspected for the requested tolerance.

The modulus rows are downstream of that inspection. The uniform-modulus composition and Dini or compact-uniform handoff rows $M,U$ must be replayed before a sup-norm comparison is visible.

The comparison row $S$ is the only route to the Real-sealed sup-norm bound. The structural rows $H,C,P,N$ preserve that finite route under transport and replay, so no host function equality, infinite hull, quotient equality, choice-selected translation, compactness principle, or Real completeness theorem is exported.
\end{proof}

\begin{theorem}[AlmostPeriodic ledger nonescape]
\label{thm:almost-periodic-ledger-nonescape}
Every $\AlmostPeriodicUp$ consumer read is generated by the rows named in \autoref{def:almost-periodic-carrier}. In particular, the packet exports no Bohr compactification, no completed translation hull, no host equality of functions, no quotient function-space equality, no choice-selected period, no open-cover compactness, and no ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project an accepted carrier. Function-window reads pass through $F$, translation reads pass through $T$, relatively-dense candidate reads pass through $N_{\mathrm{rel}}$, and every comparison read passes through $S$ after the modulus rows $M,U$ have been replayed.

Transport and replay preserve only those displayed rows. Provenance and local naming record the same packet and do not add analytic coordinates.

The excluded objects are absent from the carrier. They therefore cannot be obtained by projection, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, or local naming.
\end{proof}

\closureat{AlmostPeriodicUp}{seedStr}

\begin{closurestatus}{\AlmostPeriodicUp}
  \constructivestory{An $\AlmostPeriodicUp$ packet is generated from function-window rows, translation-budget rows, relatively-dense finite-net rows, sup-norm comparison rows, uniform-modulus rows, Dini and compact-uniform handoff rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert data.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:almost-periodic-carrier}, \autoref{thm:almost-periodic-namecert-obligations}, \autoref{thm:almost-periodic-supnorm-translation-stability}, and \autoref{thm:almost-periodic-ledger-nonescape} seed the finite almost-periodic translation ledger over displayed sup-norm and uniform-modulus rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host function equality, infinite translation hull compactness, Bohr compactification, quotient function-space equality, choice-selected periods, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, translation-budget accounting, relatively-dense finite-net exposure, sup-norm comparison stability, uniform-modulus routing, sibling handoff, transport stability, and ledger non-escape for BEDC.Derived.AlmostPeriodicUp.}
\end{closurestatus}
