\chapter{A Concrete Naming Certificate for $\RegularCauchyLocatedFieldUp$}
\label{ch:concrete-instances-regular-cauchy-located-field-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyLocatedFieldUp$ packet records the L10 algebra surface available from regular Cauchy real names when every reciprocal and division read is guarded by displayed apartness. It sits over the regular rational source surface of \autoref{ch:concrete-instances-regseqrat-namecert}, finite stream windows from \autoref{ch:concrete-instances-streamname-namecert}, dyadic endpoint arithmetic from \autoref{ch:concrete-instances-dyadicratcore-namecert}, the sum route of \autoref{ch:concrete-instances-regularcauchysum-namecert}, the product route of \autoref{ch:concrete-instances-regularcauchyproduct-namecert}, the reciprocal route of \autoref{ch:concrete-instances-regular-cauchy-reciprocal-namecert}, the division route of \autoref{ch:concrete-instances-regular-cauchy-division-namecert}, the apartness and order boundary of \autoref{ch:concrete-instances-regular-cauchy-apartness-order-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names a constructive field-operation packet for real-name algebra; it does not identify quotient real equality, trichotomy, selected representatives, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy located field carrier]
\label{def:regular-cauchy-located-field-carrier}
A $\RegularCauchyLocatedFieldUp$ carrier is a finite $\BHist$ packet
$$
F=(S,W,D,A,M,I,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ lists the $\RegSeqRatUp$ source rows for the regular Cauchy names consumed by the algebra packet.
\item $W$ records the finite $\StreamNameUp$ windows opened for every source read and every operation readback.
\item $D$ records the $\DyadicRatCoreUp$ endpoint rows used for rational endpoint arithmetic, tolerance comparison, and finite lower-bound inspection.
\item $A$ is the apartness guard row from the $\RegularCauchyApartnessOrderUp$ boundary; it is required before any reciprocal or quotient route can be read.
\item $M$ is the additive and multiplicative operation inventory, consisting of $\RegularCauchySumUp$, $\RegularCauchyProductUp$, and scalar endpoint rows visible at the same window level.
\item $I$ is the guarded reciprocal route from $\RegularCauchyReciprocalUp$, read only after $A$ has displayed a positive nonzero-domain witness.
\item $Q$ is the guarded division route from $\RegularCauchyDivisionUp$, factoring quotient reads through the same apartness guard, reciprocal route, product route, and regular readback surface.
\item $E$ is the terminal $\RealUp$ seal receiving only the displayed regular Cauchy readbacks and their visible operation provenance.
\item $H$ records componentwise $\hsame$ transport for $S,W,D,A,M,I,Q,E,C,P,N$.
\item $C$ records displayed $\Cont$ replay for source inspection, window inspection, dyadic endpoint arithmetic, apartness exposure, sum and product exposure, reciprocal and division handoff, readback, and seal handoff.
\item $P$ records $\Pkg$ provenance over $\RegularCauchyLocatedFieldUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegularCauchySumUp$, $\RegularCauchyProductUp$, $\RegularCauchyReciprocalUp$, $\RegularCauchyDivisionUp$, $\RegularCauchyApartnessOrderUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyLocatedFieldUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the displayed rows $S,W,D,A,M,I,Q,E,H,C,P,N$.
\end{definition}

\begin{theorem}[Regular Cauchy located field NameCert obligations]
\label{thm:regular-cauchy-located-field-namecert-obligations}
The seed $\NameCert_{\RegularCauchyLocatedFieldUp}$ surface for \autoref{def:regular-cauchy-located-field-carrier} consists exactly of carrier admission, operation exposure, reciprocal and division reads guarded by apartness, regular readback, terminal Real seal nonescape, componentwise transport, displayed continuation replay, package provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from the displayed tuple $F=(S,W,D,A,M,I,Q,E,H,C,P,N)$. The source rows, stream windows, dyadic endpoint arithmetic, apartness guard, operation inventory, reciprocal route, division route, seal, transports, continuations, provenance, and local name are all explicit coordinates.

Operation exposure is finite. Sum and product reads are carried by $M$, while reciprocal reads are carried by $I$ and quotient reads are carried by $Q$. The reciprocal and division rows are downstream of $A$, so no inverse or quotient consumer can bypass the positive apartness guard.

Readback and seal nonescape are terminal. The route reaches $\RegSeqRatUp$ readbacks through the operation rows and then reaches $E$ as a $\RealUp$ seal; the carrier has no coordinate for quotient real equality, trichotomy, selected representatives, countable choice, or ambient completeness.

Transport, replay, and provenance are exactly $H,C,P,N$. They move and re-expose the same rows componentwise, so the local NameCert surface is exhausted by the displayed packet.
\end{proof}

\begin{theorem}[Regular Cauchy located field guarded division scope]
\label{thm:regular-cauchy-located-field-guarded-division-scope}
Every reciprocal or quotient read from an accepted $\RegularCauchyLocatedFieldUp$ packet factors through
$$
S,W,D \longmapsto A \longmapsto I,Q \longmapsto E,H,C,P,N.
$$
The field-operation packet therefore exposes guarded real-name algebra only through finite regular Cauchy source data, dyadic endpoint arithmetic, apartness evidence, reciprocal and division handoffs, and the terminal $\RealUp$ seal.
\end{theorem}
\begin{proof}
Project the packet. The rows $S,W,D$ supply the visible regular source data, stream windows, and endpoint arithmetic used by every operation read.

The guard row $A$ is the only coordinate that licenses reciprocal or division access. Hence $I$ and $Q$ can be read only after the apartness boundary has been displayed.

The terminal rows $E,H,C,P,N$ seal and replay that finite route. Since no additional coordinate is present, the carrier cannot export total inversion, trichotomy, quotient equality, selected representatives, countable choice, or ambient completeness.
\end{proof}

\closureat{RegularCauchyLocatedFieldUp}{seedStr}

\begin{closurestatus}{\RegularCauchyLocatedFieldUp}
  \constructivestory{A $\RegularCauchyLocatedFieldUp$ packet is generated from RegSeqRat source rows, StreamName windows, DyadicRatCore endpoint arithmetic, RegularCauchySum and RegularCauchyProduct operation rows, apartness-guarded RegularCauchyReciprocal and RegularCauchyDivision rows, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-located-field-carrier}, \autoref{thm:regular-cauchy-located-field-namecert-obligations}, and \autoref{thm:regular-cauchy-located-field-guarded-division-scope} seed the constructive located-field operation boundary over regular Cauchy real names.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient real equality, trichotomy, selected representatives, countable choice, total inversion, ambient $\RealUp$ completeness, Lean verification, or standard bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, operation exposure, apartness-guarded reciprocal and division handoff, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyLocatedFieldUp.}
\end{closurestatus}
