\chapter{A Concrete Naming Certificate for $\CompactLipschitzUniformHandoffUp$}
\label{ch:concrete-instances-compact-lipschitz-uniform-handoff-namecert}
\origin{human}

Following Bishop--Bridges style compact metric uniform-continuity, the $\CompactLipschitzUniformHandoffUp$ packet records the finite route by which compact finite-net data and a Lipschitz graph row supply a tolerance-only $\UniformModulusUp$ consumer. It is grounded in the compact-uniform-continuity vision of \autoref{ch:visions-compact-uniform-continuity}; it reads compact metric nets from \autoref{ch:concrete-instances-compactmetric-namecert}, continuous graph rows from \autoref{ch:concrete-instances-continuousmap-namecert}, dyadic tolerance rows from \autoref{ch:concrete-instances-dyadicratcore-namecert}, rational lower-bound comparison from \autoref{ch:concrete-instances-rat-namecert}, the uniform-modulus handoff of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter packages the finite-net, Lipschitz graph, tolerance-fold, and uniform-modulus route without importing choice, open-cover compactness, quotient function equality, or ambient $\RealUp$ completeness.

\begin{definition}[Compact Lipschitz uniform handoff carrier]
\label{def:compact-lipschitz-uniform-handoff-carrier}
A $\CompactLipschitzUniformHandoffUp$ carrier is a finite $\BHist$ packet
$$
L=(K,G,T,R,U,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ finite-net row, exposing a finite $\mathsf{ProbeBundle}$ of compact source centers at the requested tolerance scale.
\item $G$ is the $\ContinuousMapUp$ graph row together with its Lipschitz ledger: one rational bound, source and target metric rows, and the graph-distance implication consumed by the uniform estimate.
\item $T$ is the $\DyadicRatCoreUp$ tolerance row, carrying endpoint windows for the requested target tolerance and the derived source radius.
\item $R$ is the $\RatUp$ lower-bound fold over the finite list of compact-net radii and Lipschitz-derived source radii.
\item $U$ is the $\UniformModulusUp$ handoff row exported to downstream compact-continuous consumers.
\item $E$ is the terminal $\RealUp$ seal, reached only after the compact net, graph, tolerance, rational fold, and uniform-modulus rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for $K,G,T,R,U,E,C,P,N$.
\item $C$ records displayed $\Cont$ replay for compact finite-net inspection, graph and Lipschitz inspection, dyadic tolerance comparison, rational lower-bound folding, uniform-modulus handoff, and seal handoff.
\item $P$ records $\Pkg$ provenance over $\CompactLipschitzUniformHandoffUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\DyadicRatCoreUp$, $\RatUp$, $\UniformModulusUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactLipschitzUniformHandoffUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the rows $K,G,T,R,U,E,H,C,P,N$.
\end{definition}

\begin{theorem}[Compact Lipschitz uniform handoff NameCert obligations]
\label{thm:compact-lipschitz-uniform-handoff-namecert-obligations}
The seed $\NameCert_{\CompactLipschitzUniformHandoffUp}$ surface for \autoref{def:compact-lipschitz-uniform-handoff-carrier} consists exactly of carrier admission, compact finite-net exposure, continuous graph and Lipschitz ledger exposure, dyadic tolerance inspection, rational lower-bound folding, $\UniformModulusUp$ handoff, terminal Real seal nonescape, componentwise transport, displayed continuation replay, package provenance, and the local naming row.
\end{theorem}
\begin{proof}
Carrier admission is projection from $L=(K,G,T,R,U,E,H,C,P,N)$. The compact metric net, graph and Lipschitz row, dyadic tolerance row, rational fold, uniform-modulus handoff, seal, transports, continuations, provenance, and local name are explicit coordinates.

The analytic route is finite. The compact row $K$ supplies only the listed $\mathsf{ProbeBundle}$ centers, the graph row $G$ supplies the Lipschitz estimate at those source distances, and the tolerance row $T$ supplies the dyadic scale consumed by the lower-bound fold $R$.

The uniform-modulus row $U$ is downstream of $K,G,T,R$. It can therefore be replayed only after the finite-net and Lipschitz ledger have fixed the source precision. The seal $E$ receives this handoff without adding open-cover compactness, selected moduli, quotient function equality, or ambient completeness.

Transport, replay, and provenance are exactly $H,C,P,N$. Componentwise $\hsame$ and displayed $\Cont$ rows re-expose the same finite route, so the NameCert obligations are exhausted by the carrier.
\end{proof}

\begin{theorem}[Compact Lipschitz uniform consumer route]
\label{thm:compact-lipschitz-uniform-consumer-route}
Every $\UniformModulusUp$ consumer of an accepted $\CompactLipschitzUniformHandoffUp$ packet factors through
$$
K,G,T \longmapsto R \longmapsto U \longmapsto E,H,C,P,N.
$$
Thus the exported modulus is a finite compact-net and Lipschitz-ledger handoff, not a choice functional, not an open-cover argument, and not a quotient-function equality principle.
\end{theorem}
\begin{proof}
Read the compact source row $K$ and graph row $G$ first. These rows expose the finite centers, source and target metric data, and Lipschitz bound needed by the consumer route.

Use the dyadic tolerance row $T$ to form the rational comparison scale. The finite lower-bound fold $R$ is computed over the displayed compact-net and Lipschitz-derived radii, so it is a $\RatUp$ ledger rather than an external selector.

The uniform-modulus row $U$ is then the only exported consumer row. The remaining rows $E,H,C,P,N$ seal, transport, replay, source, and name this same finite route, leaving no coordinate for open-cover compactness, countable choice, selected moduli, quotient function equality, or ambient $\RealUp$ completeness.
\end{proof}

\closureat{CompactLipschitzUniformHandoffUp}{seedStr}

\begin{closurestatus}{\CompactLipschitzUniformHandoffUp}
  \constructivestory{A $\CompactLipschitzUniformHandoffUp$ packet is generated from CompactMetric finite-net rows, a ContinuousMap graph with Lipschitz ledger, DyadicRatCore tolerance rows, a RatUp lower-bound fold, a UniformModulus handoff, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-lipschitz-uniform-handoff-carrier}, \autoref{thm:compact-lipschitz-uniform-handoff-namecert-obligations}, and \autoref{thm:compact-lipschitz-uniform-consumer-route} seed the finite compact-net and Lipschitz-ledger route into a UniformModulus consumer.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected moduli, countable choice, quotient function equality, ambient $\RealUp$ completeness, Lean verification, or standard bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite-net exposure, Lipschitz graph exposure, tolerance folding, UniformModulus handoff, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CompactLipschitzUniformHandoffUp.}
\end{closurestatus}
