\chapter{A Concrete Naming Certificate for $\FiniteModulusCompactUniformEquicontinuityUp$}
\label{ch:concrete-instances-finite-modulus-compact-uniform-equicontinuity-namecert}
\origin{human}

Following Bishop and Bridges on compact metric uniform continuity and equicontinuous families, the $\FiniteModulusCompactUniformEquicontinuityUp$ packet records the finite-modulus route from compact source nets to one family-level uniform equicontinuity ledger. It realizes the compact-uniform-continuity pressure of \autoref{ch:visions-compact-uniform-continuity} over the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, continuous-map observations from \autoref{ch:concrete-instances-continuousmap-namecert}, metric distance rows from \autoref{ch:concrete-instances-metric-namecert}, finite observation windows from \autoref{ch:concrete-instances-streamname-namecert}, regular rational readback from \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet exposes finite moduli and compact-net rows only; it does not import open-cover compactness, selected subcovers, host function equality, quotient map equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[FiniteModulusCompactUniformEquicontinuity carrier]
\label{def:finite-modulus-compact-uniform-equicontinuity-carrier}
A $\FiniteModulusCompactUniformEquicontinuityUp$ carrier is a finite $\BHist$ packet
$$
E=(K,F,M,U,D,S,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ finite-net row, carrying inspected centers, coverage radii, and located compact source data.
\item $F$ is the $\ContinuousMapUp$ family row, exposing the displayed finite family observations used by the equicontinuity request.
\item $M$ is the finite-modulus row assigning local source-distance budgets to the family observations at the compact-net centers.
\item $U$ is the compact-uniform equicontinuity export row, giving one displayed uniform modulus for all members of the inspected family.
\item $D$ is the $\MetricUp$ distance row for source and target comparisons used by the finite-modulus test.
\item $S$ is the $\StreamNameUp$ finite-window row selecting compact-net centers, family observations, modulus requests, and distance reads.
\item $Q$ is the $\RegSeqRatUp$ readback row for radii, distances, and modulus comparisons.
\item $R$ is the terminal $\RealUp$ seal row for compact-uniform consumers after $S$ and $Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for compact nets, continuous family rows, finite moduli, uniform export, metric distances, stream windows, regular readback, Real sealing, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from compact-net and family-modulus requests to the uniform equicontinuity export.
\item $P$ is the $\Pkg$ provenance over $\FiniteModulusCompactUniformEquicontinuityUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteModulusCompactUniformEquicontinuityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an open-cover proof, selected subcover, unrestricted host function equality, quotient map equality, countable choice, or ambient Real completeness.
\end{definition}

\begin{theorem}[FiniteModulusCompactUniformEquicontinuity NameCert obligations]
\label{thm:finite-modulus-compact-uniform-equicontinuity-namecert-obligations}
For every accepted $\FiniteModulusCompactUniformEquicontinuityUp$ carrier $E=(K,F,M,U,D,S,Q,R,H,C,P,N)$, the local $\NameCert_{\FiniteModulusCompactUniformEquicontinuityUp}$ surface consists exactly of compact finite-net admission through $K$, continuous-family observations through $F$, finite-modulus control through $M$, compact-uniform export through $U$, metric-distance inspection through $D$, StreamName windows, RegSeqRat readback, Real sealing, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-modulus-compact-uniform-equicontinuity-carrier}. The compact source row $K$, family row $F$, finite-modulus row $M$, export row $U$, and metric row $D$ are the only mathematical coordinates available to the local certificate.

The numerical route is finite. Rows $S$ and $Q$ display the selected observation windows and rational comparisons before $R$ seals the Real-facing distance reads.

The structural rows $H,C,P,N$ transport, replay, source, and name the same packet. Since the carrier has no row for open covers, selected subcovers, host function equality, quotient map equality, countable choice, or ambient Real completeness, none of those objects is part of the obligation surface.
\end{proof}

\begin{theorem}[Finite-modulus compact-uniform equicontinuity route]
\label{thm:finite-modulus-compact-uniform-equicontinuity-route}
Every compact-uniform or Arzela--Ascoli consumer of an accepted $\FiniteModulusCompactUniformEquicontinuityUp$ packet factors through
$$
K,F,D \longmapsto M \longmapsto S,Q \longmapsto R,U \longmapsto H,C,P,N .
$$
Thus the consumer reads compact finite nets, continuous family observations, and metric distances before the finite modulus is exported, and reaches the Real seal and uniform equicontinuity row only after StreamName windows and regular rational readback are visible.
\end{theorem}
\begin{proof}
Start with the compact source, family, and metric rows. The compact-net data in $K$, the continuous-family observations in $F$, and the distance comparisons in $D$ determine the finite family-modulus requests.

Next read the finite-modulus row $M$. It is the only coordinate that binds the finitely many compact-net and family observations to a common source-distance budget, so it cannot be replaced by open-cover compactness or a selected subcover.

Finally pass through $S,Q,R,U,H,C,P,N$. StreamName windows and RegSeqRat readback expose the numerical comparisons before the Real seal and uniform export are consumed, and the structural rows keep the route inside the same finite packet.
\end{proof}

\closureat{FiniteModulusCompactUniformEquicontinuityUp}{seedStr}

\begin{closurestatus}{\FiniteModulusCompactUniformEquicontinuityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-modulus-compact-uniform-equicontinuity-carrier}, \autoref{thm:finite-modulus-compact-uniform-equicontinuity-namecert-obligations}, and \autoref{thm:finite-modulus-compact-uniform-equicontinuity-route} seed the finite-modulus compact-uniform equicontinuity route over compact metric nets, continuous family observations, metric distances, StreamName windows, RegSeqRat readback, Real sealing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, open-cover compactness, selected subcovers, host function equality, quotient map equality, countable choice, standard bridge checking, or ambient Real completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-net coverage, continuous-family observation, finite-modulus control, compact-uniform export, metric-distance inspection, StreamName windows, RegSeqRat readback, Real sealing, transport, replay, provenance, and local naming for BEDC.Derived.CompactUniformEquicontinuityUp.}
  \constructivestory{A $\FiniteModulusCompactUniformEquicontinuityUp$ packet is generated from CompactMetric finite nets, ContinuousMap family observations, a finite modulus row, a compact-uniform equicontinuity export, Metric distance rows, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
