\chapter{A Concrete Naming Certificate for $\FiniteWindowBaireCategoryUp$}
\label{ch:concrete-instances-finite-window-baire-category-namecert}
\origin{human}

Following Baire and Osgood, the $\FiniteWindowBaireCategoryUp$ packet records the finite window of the Baire-category construction that a completion-facing consumer can inspect before any ambient theorem about residual sets is available. It sits over the complete-metric Baire surface of \autoref{ch:concrete-instances-complete-metric-baire-surface-namecert}, the complete-metric service of \autoref{ch:concrete-instances-completemetric-namecert}, the convergence ledger of \autoref{ch:concrete-instances-real-modulus-of-convergence-namecert}, the pointwise stream metric route of \autoref{ch:concrete-instances-pointwise-stream-metric-namecert}, and the nested-ball completion neighbor \autoref{ch:concrete-instances-complete-metric-nested-balls-namecert}. The packet is a finite-means dense-open route for Real and Completion consumers; it is not a countable-choice selector, arbitrary open-cover compactness theorem, quotient stream equality, host completeness assertion, or selected generic point.

\begin{definition}[Finite-window Baire category carrier]
\label{def:finite-window-baire-category-carrier}
A $\FiniteWindowBaireCategoryUp$ carrier is a finite $\BHist$ packet
$$
W=(M,U,D,Q,S,R,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the complete metric source row. It exposes only the complete-metric service already named by $\CompleteMetricUp$ and the metric-distance rows consumed by the window.
\item $U$ is the nested dense-open window. It records a finite prefix of dense-open requests, the displayed ball-refinement clauses, and the order in which those clauses are read.
\item $D$ is the dyadic radius ledger. It stores the finite sequence of positive dyadic radii, their shrink comparisons, and the lower-radius bounds needed before the next dense-open request is inspected.
\item $Q$ is the finite center and ball ledger. It records the named center histories, ball inclusions, and branch-local containment rows produced by the complete-metric source.
\item $S$ is the $\StreamNameUp$ schedule row for the center and radius observations.
\item $R$ is the $\RegSeqRatUp$ readback row assembled from the scheduled finite observations and the dyadic radius ledger.
\item $E$ is the $\RealUp$ seal row reached only after $M,U,D,Q,S,R$ have been displayed.
\item $T$ is the completion transport row. It records the consumer-facing route from the complete-metric source to the Real seal without replacing the source by a host completeness theorem.
\item $H$ records componentwise $\hsame$ transport for complete-metric rows, dense-open windows, dyadic radius ledgers, center ledgers, stream schedules, regular readbacks, Real seals, completion transport, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a finite Baire-window request through $M,U,D,Q,S,R,E,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteWindowBaireCategoryUp$, $\CompleteMetricBaireSurfaceUp$, $\CompleteMetricUp$, $\BaireCategoryUp$, $\RealModulusOfConvergenceUp$, $\PointwiseStreamMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteWindowBaireCategoryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $M,U,D,Q,S,R,E,T,H,C,P,N$. It has no coordinate for countable choice, arbitrary open-cover compactness, quotient stream equality, host completeness, selected generic points, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Finite-window Baire category NameCert obligations]
\label{thm:finite-window-baire-category-namecert-obligations}
For every accepted $\FiniteWindowBaireCategoryUp$ carrier
$$
W=(M,U,D,Q,S,R,E,T,H,C,P,N),
$$
the local $\NameCert_{\FiniteWindowBaireCategoryUp}$ surface consists exactly of complete-metric source exposure through $M$, nested dense-open finite-window exposure through $U$, dyadic radius-ledger exactness through $D$, finite center and ball routing through $Q$, $\StreamNameUp$ scheduling through $S$, $\RegSeqRatUp$ readback through $R$, $\RealUp$ sealing through $E$, completion transport through $T$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-baire-category-carrier}. The projection displays the complete-metric source, the dense-open window, the dyadic radius ledger, the center and ball ledger, the stream schedule, the regular readback, the Real seal, and the structural transport, replay, provenance, and naming rows.

The dense-open part is finite. Row $U$ gives only the displayed prefix of dense-open requests, while $D$ and $Q$ record the radius shrinkage and center-ball refinements used by that prefix. Thus a consumer cannot replace the window by a host countable intersection or an arbitrary open-cover compactness theorem.

The Real-facing part is downstream. Rows $S$ and $R$ schedule and repack the finite observations, and $E$ is read only after that regular-rational route is visible. The completion transport row $T$ preserves the same displayed source rather than adding a separate host-completeness claim.

Finally $H,C,P,N$ transport, replay, source, and name exactly those rows. Since the carrier contains no countable-choice selector, quotient stream coordinate, host completeness field, or selected generic point, the listed rows exhaust the NameCert obligations.
\end{proof}

\closureat{FiniteWindowBaireCategoryUp}{seedStr}

\begin{closurestatus}{\FiniteWindowBaireCategoryUp}
  \constructivestory{A $\FiniteWindowBaireCategoryUp$ packet is generated from a complete metric source row, nested dense-open finite windows, a dyadic radius ledger, finite center and ball rows, StreamName schedules, RegSeqRat readback, a RealUp seal, completion transport, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-window-baire-category-carrier} and \autoref{thm:finite-window-baire-category-namecert-obligations} seed the finite Baire dense-open window consumed by Real and Completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, arbitrary open-cover compactness, quotient stream equality, host completeness, selected generic points, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-open window exposure, dyadic radius-ledger exactness, StreamName scheduling, RegSeqRat readback, Real sealing, completion transport, provenance, and local naming for BEDC.Derived.FiniteWindowBaireCategoryUp.}
\end{closurestatus}
