\chapter{A Concrete Naming Certificate for $\DedekindCutArithmeticUp$}
\label{ch:concrete-instances-dedekind-cut-arithmetic-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\DedekindCutArithmeticUp$ packet records the finite arithmetic surface of rounded located cuts before any consumer compares it with the regular Cauchy real-name route. It sits after the rounded cut interface of \autoref{ch:concrete-instances-dedekindcut-namecert}, the Cauchy comparison boundary of \autoref{ch:concrete-instances-dedekind-cauchy-comparison-namecert}, the located cut stream of \autoref{ch:concrete-instances-dedekind-cut-stream-namecert}, and the regular real-name route of \autoref{ch:concrete-instances-regseqrat-namecert} and \autoref{ch:concrete-instances-real-namecert}. The packet names addition, negation, order, and multiplication reads as finite cut-side ledgers; it does not construct $\RealUp$ by cuts, identify quotient cuts, choose suprema, or assert completeness.

\begin{definition}[Dedekind cut arithmetic carrier]
\label{def:dedekind-cut-arithmetic-carrier}
A $\DedekindCutArithmeticUp$ carrier is a finite $\BHist$ packet
$$
A=(D,L,U,Q,S,R,E,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the source $\DedekindCutUp$ row, carrying the lower and upper rounded located cut observations.
\item $L$ is the lower arithmetic ledger, recording finite lower-side witnesses for cut addition, negation, order, and multiplication requests.
\item $U$ is the upper arithmetic ledger, recording the corresponding upper-side witnesses and disjointness guards.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance and rational-operation row used to compare the arithmetic ledgers with regular rational readback.
\item $S$ is the $\StreamNameUp$ finite-window row through which arithmetic observations are sampled.
\item $R$ is the $\RegSeqRatUp$ readback row obtained only after $D,L,U,Q,S$ are displayed.
\item $E$ is the $\RealUp$ seal row reached by the regular Cauchy route, not by a quotient-cut construction.
\item $O$ is the operation-admission ledger naming which displayed cut-side arithmetic requests have compatible regular-Cauchy readbacks.
\item $H$ records componentwise $\hsame$ transport for cut, arithmetic, dyadic, stream, readback, seal, operation, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an arithmetic request through $D,L,U,Q,S,R,E,O,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DedekindCutArithmeticUp$, $\DedekindCutUp$, $\DedekindCauchyComparisonUp$, $\DedekindCutStreamUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DedekindCutArithmeticUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these displayed rows. It has no coordinate for quotient-cut equality, host real equality, selected suprema, trichotomy, countable choice, or ambient completeness.
\end{definition}

\begin{theorem}[Dedekind cut arithmetic NameCert obligations]
\label{thm:dedekind-cut-arithmetic-namecert-obligations}
For every accepted $\DedekindCutArithmeticUp$ carrier $A=(D,L,U,Q,S,R,E,O,H,C,P,N)$, the local $\NameCert_{\DedekindCutArithmeticUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the cut source row $D$, lower and upper arithmetic ledgers $L,U$, dyadic tolerance row $Q$, stream window row $S$, regular readback row $R$, real seal row $E$, operation-admission row $O$, transport row $H$, continuation row $C$, provenance row $P$, and local naming row $N$;
\item cut-side operation discipline, requiring every arithmetic request to expose the lower and upper observation ledgers $L,U$ over the same rounded located cut row $D$;
\item dyadic tolerance discipline, requiring each arithmetic comparison to consume $Q$ before any regular readback or Real-facing seal is read;
\item stream and regular-readback discipline, requiring $S$ and $R$ to mediate all Cauchy-facing arithmetic reads;
\item operation-admission exactness, requiring $O$ to name only those cut-side operation rows whose regular-Cauchy readback has passed through $D,L,U,Q,S,R,E$;
\item non-escape, requiring $P,N$ to export no quotient-cut equality, host real equality, selected supremum, trichotomy, countable-choice selector, Dedekind construction of $\RealUp$, or ambient completeness theorem.
\end{enumerate}
No local arithmetic obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dedekind-cut-arithmetic-carrier}. The accepted packet exposes exactly the cut source, lower and upper arithmetic ledgers, dyadic tolerance, stream window, regular readback, real seal, operation admission, transport, replay, provenance, and local naming rows.

The cut-side operation discipline is read from $D,L,U$. Each arithmetic request is named by lower and upper observation ledgers over the same rounded located cut source, so no operation can substitute a quotient cut or a host real representative.

The Cauchy-facing discipline is read from $Q,S,R,E$. The dyadic row supplies the tolerance budget, the stream row opens finite observation windows, the regular readback row exposes rational Cauchy data, and the seal row is reached only after that route is displayed.

Finally $O,H,C,P,N$ admit, transport, replay, source, and name only the same finite route. Since the carrier has no excluded coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Dedekind cut arithmetic Cauchy compatibility]
\label{thm:dedekind-cut-arithmetic-cauchy-compatibility}
Every $\RealUp$-facing consumer of an accepted $\DedekindCutArithmeticUp$ carrier that reads a cut-side arithmetic operation must factor through
$$
\DedekindCutUp,\ \DedekindCauchyComparisonUp,\ \DedekindCutStreamUp,\ \DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
The consumer first reads the displayed lower and upper cut arithmetic ledgers $L,U$ over $D$, then the dyadic tolerance row $Q$, then the stream and regular-readback rows $S,R$, and only then the Real seal row $E$ and operation-admission row $O$. The route supplies compatibility of displayed cut-side operations with displayed regular-Cauchy readback; it supplies no quotient-cut arithmetic, no quotient real equality, no selected supremum, no trichotomy branch, no countable choice, and no completeness theorem.
\end{theorem}
\begin{proof}
Open an accepted carrier $A=(D,L,U,Q,S,R,E,O,H,C,P,N)$. The only cut-side arithmetic data are the lower and upper ledgers $L,U$ over the displayed rounded located cut row $D$.

To compare this arithmetic data with the regular Cauchy route, the packet must expose the dyadic tolerance row $Q$ and the finite observation windows $S$. The readback row $R$ is downstream of those rows, and the Real seal $E$ is downstream of $R$.

The comparison boundary is therefore the same finite route named by the Dedekind-Cauchy and Dedekind-cut stream packets: cut observations are sampled through finite stream windows and then read as regular rational data before the terminal Real seal is available.

The operation-admission row $O$ records only arithmetic requests that have passed through that route, while $H,C,P,N$ transport, replay, source, and name the same data. Since no quotient-cut, quotient-real, selected-supremum, trichotomy, choice, or completeness coordinate occurs in the carrier, every Real-facing arithmetic read has exactly the displayed Cauchy-compatible boundary.
\end{proof}

\closureat{DedekindCutArithmeticUp}{seedStr}

\begin{closurestatus}{\DedekindCutArithmeticUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dedekind-cut-arithmetic-carrier}, \autoref{thm:dedekind-cut-arithmetic-namecert-obligations}, and \autoref{thm:dedekind-cut-arithmetic-cauchy-compatibility} seed the cut arithmetic route over DedekindCutUp, DedekindCauchyComparisonUp, DedekindCutStreamUp, DyadicRatCoreUp, StreamNameUp, RegSeqRatUp, RealUp, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient-cut arithmetic, quotient real equality, selected suprema, trichotomy, countable choice, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, cut-side operation discipline, dyadic tolerance discipline, stream and regular-readback discipline, operation-admission exactness, and non-escape proofs for BEDC.Derived.DedekindCutArithmeticUp.}
  \constructivestory{A $\DedekindCutArithmeticUp$ packet is generated from a DedekindCut row, lower and upper arithmetic ledgers, a DyadicRatCore tolerance row, StreamName finite windows, RegSeqRat readback, a RealUp seal, an operation-admission row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
\end{closurestatus}
