\chapter{A Concrete Naming Certificate for $\RegularCauchyDiagonalLimitUp$}
\label{ch:concrete-instances-regular-cauchy-diagonal-limit-namecert}
\origin{human}

Bishop--Bridges style diagonal arguments turn a displayed family of regular Cauchy rational names into a limit-facing regular read by synchronizing finite windows and tolerance ledgers before any real seal is exposed. The $\RegularCauchyDiagonalLimitUp$ packet records that consumer route as one finite NameCert surface. It sits after the $\StreamNameUp$ window interface of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, and the regular-Cauchy diagonal sibling of \autoref{ch:concrete-instances-regular-cauchy-diagonal-extraction-namecert}. The packet names the L10 diagonal-limit consumer for regular rational sequences and real-name seals; it is not quotient stream equality, a host-selected limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy diagonal limit carrier]
\label{def:regular-cauchy-diagonal-limit-carrier}
A $\RegularCauchyDiagonalLimitUp$ carrier is a finite $\BHist$ packet
$$
D=(S,W,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the displayed source-family row of regular Cauchy rational names whose diagonal entries may be inspected.
\item $W$ is the synchronized $\StreamNameUp$ window family for the source row, diagonal selector reads, and limit-facing output read.
\item $R$ is the $\RegSeqRatUp$ diagonal readback row assembled from the accepted source windows.
\item $Q$ is the $\DyadicRatCoreUp$ tolerance, slack, and comparison ledger used to align the source windows with the diagonal readback.
\item $E$ is the terminal $\RealUp$ seal row, exposed only after $S,W,R,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the source family, synchronized windows, regular readback, dyadic ledger, real seal, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each limit-facing precision request through $S,W,Q,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyDiagonalLimitUp$, $\RegularCauchyDiagonalExtractionUp$, $\RegularCauchyDiagonalWindowUp$, $\RegularCauchyDiagonalSealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyDiagonalLimitUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,W,R,Q,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected representatives, countable-choice schedules, host limits, trichotomy, ambient completeness, Lean verification, or bridge credentials.
\end{definition}

\begin{theorem}[Regular Cauchy diagonal limit NameCert obligations]
\label{thm:regular-cauchy-diagonal-limit-namecert-obligations}
For every accepted $\RegularCauchyDiagonalLimitUp$ carrier
$$
D=(S,W,R,Q,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyDiagonalLimitUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the source family, synchronized windows, regular readback, dyadic tolerance ledger, terminal real seal, transport, replay, provenance, and local naming rows;
\item window coverage, requiring every limit-facing request to read only windows listed in $W$ and only source data displayed by $S$;
\item dyadic exactness, requiring $Q$ to be the sole tolerance, slack, and comparison ledger used to align the diagonal readback;
\item RegSeqRat handoff, requiring $R$ to be downstream of $S,W,Q$ and upstream of the terminal real seal $E$;
\item Real seal non-escape, requiring $E,H,C,P,N$ to expose no quotient stream equality, host-selected limit, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge credential.
\end{enumerate}
No Regular Cauchy diagonal-limit obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:regular-cauchy-diagonal-limit-carrier}. The displayed tuple $S,W,R,Q,E,H,C,P,N$ is the entire public surface, so carrier admission is exactly admission of those rows.

The window and dyadic clauses are read next. A limit-facing request enters through the synchronized window family $W$, while $Q$ supplies the tolerance, slack, and comparison cells attached to that window. The source-family row $S$ is inspected only through those displayed windows.

The regular readback row $R$ is therefore downstream of $S,W,Q$. Once $R$ has been displayed, the seal row $E$ may be read as a $\RealUp$ boundary, and the structural rows $H,C,P,N$ transport, replay, source, and name the same route.

Because the carrier has no further coordinate, the excluded analytic and choice-theoretic objects cannot be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal limit RegSeqRat handoff]
\label{thm:regular-cauchy-diagonal-limit-regseqrat-handoff}
Every $\RealUp$-facing consumer of an accepted $\RegularCauchyDiagonalLimitUp$ carrier first reads the finite route
$$
S,W,Q \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
Thus the L10 diagonal route hands off a $\RegSeqRatUp$ readback before the real seal is available, and the consumer receives no quotient stream equality, selected limit, countable-choice schedule, trichotomy row, host real equality, or ambient $\RealUp$ completeness coordinate.
\end{theorem}
\begin{proof}
Start from a limit-facing request. The carrier admits no direct read of the real seal, so the request must first pass through the source row $S$, the synchronized windows $W$, and the dyadic tolerance ledger $Q$.

These rows assemble the regular rational diagonal readback $R$. The readback is the only row that can feed the terminal $\RealUp$ seal $E$, so any consumer reaching the seal has already consumed the RegSeqRat handoff.

The rows $H,C,P,N$ preserve this displayed route under transport, replay, provenance, and local naming. Since no excluded coordinate occurs in the carrier, the handoff exports only the finite diagonal-limit packet.
\end{proof}

\falsifiablePrediction{Every $\RegularCauchyDiagonalLimitUp$ Real-facing read factors through a displayed source family, synchronized StreamName windows, one DyadicRatCore tolerance ledger, one RegSeqRat diagonal readback, one terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, regular-cauchy-diagonal-extraction, regular-cauchy-diagonal-window, regular-cauchy-diagonal-seal: $\RegularCauchyDiagonalLimitUp$ is not bijective to any listed sibling because it jointly carries the limit-facing source family, synchronized windows, tolerance ledger, RegSeqRat handoff, Real seal, transport, replay, provenance, and local naming in one packet.}

\closureat{RegularCauchyDiagonalLimitUp}{seedStr}

\begin{closurestatus}{\RegularCauchyDiagonalLimitUp}
  \constructivestory{A $\RegularCauchyDiagonalLimitUp$ packet is generated from a regular Cauchy source family, synchronized StreamName windows, a DyadicRatCore tolerance ledger, a RegSeqRat diagonal readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-diagonal-limit-carrier}, \autoref{thm:regular-cauchy-diagonal-limit-namecert-obligations}, and \autoref{thm:regular-cauchy-diagonal-limit-regseqrat-handoff} seed the finite diagonal-limit route from regular Cauchy source windows through RegSeqRat readback to a terminal RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected limits, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, window coverage, dyadic exactness, RegSeqRat handoff, Real seal non-escape, componentwise transport, displayed replay, and local naming for BEDC.Derived.RegularCauchyDiagonalLimitUp.}
\end{closurestatus}
