\chapter{A Concrete Naming Certificate for $\RegularCauchyOscillationUp$}
\label{ch:concrete-instances-regular-cauchy-oscillation-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularCauchyOscillationUp$ packet records the finite oscillation control carried by a regular Cauchy rational name before a Real or completion-facing consumer may read the terminal seal. It sits after the tail-variation ledger of \autoref{ch:concrete-instances-cauchyoscillation-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the Cauchy modulus surface of \autoref{ch:concrete-instances-cauchymodulus-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is an L10 NameCert surface for regular-Cauchy oscillation arguments, not quotient stream equality, a selected limit, countable choice, trichotomy, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy oscillation carrier]
\label{def:regular-cauchy-oscillation-carrier}
A $\RegularCauchyOscillationUp$ carrier is a finite $\BHist$ packet
$$
O=(S,W,Q,D,L,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ schedule selecting the inspected source indices, tail windows, and comparison pairs used by the oscillation request.
\item $W$ is the finite window ledger synchronized with $S$ and with the requested Cauchy-modulus thresholds.
\item $Q$ is the $\RegSeqRatUp$ readback row for the regular rational sequence observed through the displayed windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance, slack, and comparison row used to measure the tail oscillation.
\item $L$ is the $\CauchyOscillationUp$ ledger, recording the displayed tail-diameter comparisons read from $S,W,Q,D$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the StreamName schedule, RegSeqRat readback, dyadic tolerance row, and oscillation ledger have been displayed.
\item $H$ records componentwise $\hsame$ transport for the schedule, windows, readback, tolerance, oscillation ledger, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each Real or completion-facing oscillation request through $S,W,Q,D,L,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyOscillationUp$, $\CauchyOscillationUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CauchyModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchyOscillationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,W,Q,D,L,E,H,C,P,N$. It has no coordinate for quotient stream equality, host real equality, selected limits, countable choice, trichotomy, ambient completeness, Lean verification, or bridge credentials.
\end{definition}

\begin{theorem}[Regular Cauchy oscillation NameCert obligations]
\label{thm:regular-cauchy-oscillation-namecert-obligations}
For every accepted $\RegularCauchyOscillationUp$ carrier
$$
O=(S,W,Q,D,L,E,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyOscillationUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the StreamName schedule, finite windows, RegSeqRat readback, DyadicRatCore tolerance row, CauchyOscillation ledger, Real seal, transport, replay, provenance, and local name;
\item schedule coverage, requiring every inspected index and tail pair to be named by $S$ and opened through a window in $W$;
\item dyadic tolerance exactness, requiring every oscillation comparison to consume its tolerance and slack cells from $D$;
\item Cauchy-modulus compatibility, requiring the tail threshold read through $\CauchyModulusUp$ to be attached to the same $S,W,Q,D$ route;
\item Real seal non-escape, requiring $E,H,C,P,N$ to expose no quotient stream equality, host real equality, selected limit, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge credential.
\end{enumerate}
No Regular Cauchy oscillation obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:regular-cauchy-oscillation-carrier}. The displayed tuple $S,W,Q,D,L,E,H,C,P,N$ is the entire public surface, so carrier admission is exactly admission of those rows.

The schedule and dyadic clauses are read next. The row $S$ names the inspected indices and tail pairs, $W$ opens the corresponding finite windows, and $D$ supplies the tolerance and slack cells used by each comparison.

The oscillation ledger $L$ is downstream of $S,W,Q,D$. Its Cauchy-modulus compatibility is therefore a finite route through the same schedule, windows, regular readback, and dyadic tolerance cells before the terminal seal $E$ can be consumed.

The structural rows $H,C,P,N$ transport, replay, source, and name only this route. Since the carrier contains no further coordinate, the excluded quotient, choice, order, completeness, verification, and bridge objects cannot be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[Regular Cauchy oscillation Real handoff]
\label{thm:regular-cauchy-oscillation-real-handoff}
Every $\RealUp$ or completion-facing consumer of an accepted $\RegularCauchyOscillationUp$ carrier first reads the finite route
$$
S,W,Q,D \longmapsto L \longmapsto E \longmapsto H,C,P,N .
$$
Thus the consumer receives a displayed StreamName schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, CauchyOscillation row, Real seal, transport, replay, provenance, and local NameCert before it can treat the regular Cauchy name as a real-facing source. It receives no quotient stream equality, host real equality, selected limit, countable-choice schedule, trichotomy row, ambient $\RealUp$ completeness coordinate, Lean verification, or bridge credential.
\end{theorem}
\begin{proof}
Start with a Real or completion-facing request. The carrier has no direct path to the real seal, so the request must first open the schedule $S$, the finite windows $W$, the regular rational readback $Q$, and the dyadic tolerance row $D$.

These rows determine the oscillation ledger $L$. The ledger is the only row that records the tail comparison needed before the terminal seal $E$ is exposed, so every seal read factors through the displayed oscillation route.

Transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ preserve the same route. With no quotient, choice, trichotomy, or ambient-completeness coordinate in the packet, the handoff exports only the finite regular-Cauchy oscillation surface.
\end{proof}

\falsifiablePrediction{Every $\RegularCauchyOscillationUp$ Real-facing read factors through one StreamName schedule, one finite window ledger, one RegSeqRat readback row, one DyadicRatCore tolerance row, one CauchyOscillation ledger, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchyoscillation, regseqrat, streamname, dyadicratcore, real, cauchymodulus: $\RegularCauchyOscillationUp$ is not bijective to any listed sibling because it jointly carries the regular source schedule, finite windows, regular readback, dyadic tolerance cells, Cauchy oscillation ledger, Real seal, transport, replay, provenance, and local naming in one packet.}

\closureat{RegularCauchyOscillationUp}{seedStr}

\begin{closurestatus}{\RegularCauchyOscillationUp}
  \constructivestory{A $\RegularCauchyOscillationUp$ packet is generated from a StreamName schedule, finite regular-source windows, RegSeqRat readback, DyadicRatCore tolerance cells, a CauchyOscillation ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-oscillation-carrier}, \autoref{thm:regular-cauchy-oscillation-namecert-obligations}, and \autoref{thm:regular-cauchy-oscillation-real-handoff} seed the finite regular-Cauchy oscillation route from inspected stream windows through dyadic tolerance cells, RegSeqRat readback, CauchyOscillation ledger, and RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, host real equality, selected limits, countable choice, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, schedule coverage, dyadic tolerance exactness, Cauchy-modulus compatibility, Real seal non-escape, transport stability, replay stability, provenance exhaustion, and local naming for BEDC.Derived.RegularCauchyOscillationUp.}
\end{closurestatus}
