\chapter{A Concrete Naming Certificate for $\VariationalEquationUp$}
\label{ch:concrete-instances-variational-equation-namecert}
\origin{human}

Following Coddington and Levinson, the $\VariationalEquationUp$ packet records the finite linearized-flow companion to the local Picard--Lindelof route. It sits after the local existence surface of \autoref{ch:concrete-instances-picard-lindelof-namecert}, the ODE source of \autoref{ch:concrete-instances-ode-namecert}, the vector-field Lipschitz ledger of \autoref{ch:concrete-instances-lipschitzmap-namecert}, the Banach state classifier of \autoref{ch:concrete-instances-banach-namecert}, and the complete-metric convergence boundary of \autoref{ch:concrete-instances-completemetric-namecert}. The packet names the tangent linear equation along one displayed local flow; it is not a global differentiable flow, a host fundamental-matrix object, a maximal interval theorem, or a choice-selected family of derivatives.

\begin{definition}[Variational equation carrier]
\label{def:variational-equation-carrier}
A $\VariationalEquationUp$ carrier is a finite $\BHist$ packet
$$
V=(B,D,L,T,U,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $B$ is the base local-flow row, read through a $\PicardLindelofUp$ packet and the underlying $\OdeUp$ time-state source.
\item $D$ is the derivative and Lipschitz ledger for the vector field on the same local window, including the displayed linearization row and the Lipschitz bound used to compare nearby tangent reads.
\item $L$ is the linearized Picard route, a finite contraction-style ledger that reads each tangent iterate through $B,D$ and the carried Banach state classifier.
\item $T$ is the tangent-transport row, recording how displayed tangent vectors are carried along the base local-flow row before the linearized endpoint is read.
\item $U$ is the uniqueness and nonescape row for the tangent equation on the named local time-state window.
\item $H$ stores componentwise $\hsame$ transport for the base flow, derivative ledger, linearized Picard route, tangent transport, uniqueness and nonescape row, replay row, provenance row, and local naming row.
\item $C$ stores the displayed $\Cont$ replay from the base local-flow row through derivative reads, tangent Picard iterates, tangent transport, uniqueness, and local endpoint comparison.
\item $P$ is the $\Pkg$ provenance over $\VariationalEquationUp$, $\PicardLindelofUp$, $\OdeUp$, $\LipschitzMapUp$, $\BanachUp$, $\CompleteMetricUp$, $\PicardContractionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\VariationalEquationUp}$ row.
\end{enumerate}
The carrier exposes only the finite tangent equation route attached to one accepted local-flow packet. It has no coordinate for a host derivative bundle, a global fundamental matrix, smooth flow dependence beyond the displayed derivative ledger, maximal continuation, or bridge-checked standardization.
\end{definition}

\begin{theorem}[Variational equation NameCert obligations]
\label{thm:variational-equation-namecert-obligations}
For an accepted $\VariationalEquationUp$ carrier
$$
V=(B,D,L,T,U,H,C,P,N),
$$
the local $\NameCert_{\VariationalEquationUp}$ surface consists exactly of base local-flow admission, derivative and Lipschitz ledger admission, linearized Picard-route compatibility, tangent-transport visibility, uniqueness and nonescape stability, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every tangent endpoint read must pass through these rows before it is treated as a linearized ODE solution.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:variational-equation-carrier}. The base flow row $B$ fixes the $\PicardLindelofUp$ and $\OdeUp$ source, while $D$ supplies the displayed derivative and Lipschitz data used by the linearized equation.

Induct over the finite linearized Picard route $L$. At the base row, the tangent iterate is attached to the displayed base flow and derivative ledger. At a successor row, the next tangent iterate is read by the same derivative ledger, the same Banach state classifier, and the same local window.

The tangent endpoint is then exposed only through $T$ and $U$. The transport row $T$ keeps tangent reads attached to the base local-flow route, and the row $U$ records the finite uniqueness and nonescape boundary.

Finally the structural rows $H,C,P,N$ transport, replay, source, and name this same route. Since no carrier coordinate contains a host derivative bundle, a global fundamental matrix, or a selected family of derivatives, the listed obligations exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Variational equation local Picard companion route]
\label{thm:variational-equation-local-picard-companion-route}
Every accepted $\VariationalEquationUp$ packet is consumed as a local linearized companion of an accepted $\PicardLindelofUp$ packet. A consumer must first read the base local-flow row $B$, the derivative and Lipschitz ledger $D$, the linearized Picard route $L$, the tangent-transport row $T$, the uniqueness and nonescape row $U$, and the structural rows $H,C,P,N$. The packet exports no tangent endpoint outside that finite base-flow route.
\end{theorem}
\begin{proof}
Project $V=(B,D,L,T,U,H,C,P,N)$. The only base trajectory available to the packet is the displayed local-flow row $B$, and the only vector-field variation available to the packet is the derivative and Lipschitz ledger $D$.

Use the finite route $L$ for tangent iteration. Each linearized iterate reads the same base flow and derivative ledger, so a consumer cannot detach the tangent equation from the accepted $\PicardLindelofUp$ route.

The endpoint-facing rows are $T$ and $U$. They record tangent transport, uniqueness, and nonescape inside the same local window, while $H,C,P,N$ preserve the route under transport, replay, provenance, and naming.
\end{proof}

\falsifiablePrediction{Every accepted $\VariationalEquationUp$ tangent endpoint read exposes one base local-flow row, one derivative and Lipschitz ledger, one linearized Picard route, one tangent-transport row, one uniqueness and nonescape row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{picard-lindelof, ode, lipschitzmap, banach, completemetric: $\VariationalEquationUp$ is not bijective to any listed sibling because it jointly carries the base local-flow row, derivative and Lipschitz ledger, linearized Picard route, tangent transport, uniqueness and nonescape row, and the transport/replay/provenance rows tying them together.}

\closureat{VariationalEquationUp}{seedStr}

\begin{closurestatus}{\VariationalEquationUp}
  \constructivestory{A $\VariationalEquationUp$ packet is generated from one PicardLindelof base local-flow row, one derivative and Lipschitz ledger, one linearized Picard route, one tangent-transport row, one uniqueness and nonescape row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:variational-equation-carrier}, \autoref{thm:variational-equation-namecert-obligations}, and \autoref{thm:variational-equation-local-picard-companion-route} seed the finite linearized ODE companion route over a displayed local Picard flow, derivative ledger, tangent transport, nonescape, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim global differentiable flow, a host fundamental matrix, maximal continuation, choice-selected derivative families, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked base-flow admission, derivative and Lipschitz ledger admission, linearized Picard-route compatibility, tangent-transport visibility, uniqueness and nonescape stability, transport, replay, provenance, and local naming for BEDC.Derived.VariationalEquationUp.}
\end{closurestatus}
