\chapter{A Concrete Naming Certificate for $\PushdownAutomatonUp$}
\label{ch:concrete-instances-pushdown-automaton-namecert}
\origin{human}

Following Hopcroft--Ullman and Sipser, the $\PushdownAutomatonUp$ packet
records a finite-control recognizer with a visible stack ledger as displayed
BEDC data. It sits between the finite run surface of
\autoref{ch:concrete-instances-finite-automaton-namecert}, the accepted-word
surface of \autoref{ch:concrete-instances-regularlanguage-namecert}, the
finite derivation surface of
\autoref{ch:concrete-instances-contextfreegrammar-namecert}, and the bounded
machine-trace surface of
\autoref{ch:concrete-instances-turingmachine-namecert}.

The packet names one finite state carrier, one input word, one stack alphabet,
one transition ledger, one finite run ledger, and one acceptance readback. It
does not identify languages extensionally, select an infinite parse tree, or
export an unbounded recognizer trace.

\begin{definition}[PushdownAutomaton carrier]
\label{def:pushdown-automaton-carrier}
A $\PushdownAutomatonUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
A=(Q,\Sigma,\Gamma,\delta,q_0,Z_0,F,w,\rho,\sigma,e,\chi,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the finite control-state carrier row;
\item $\Sigma$ is the finite input alphabet row;
\item $\Gamma$ is the finite stack alphabet row;
\item $\delta$ is the finite transition ledger, whose displayed entries read
  a state row, an optional input-symbol row, and the top stack-symbol row, then
  return the next state row and the finite stack-word replacement row;
\item $q_0$ is the start-state row inside $Q$;
\item $Z_0$ is the initial stack-symbol row inside $\Gamma$;
\item $F$ is the accepting-state row inside $Q$;
\item $w$ is the finite input word as a $\ListUp$ row over $\Sigma$;
\item $\rho$ is the finite run ledger, beginning at $(q_0,Z_0)$ and consuming
  $w$ through displayed transition rows;
\item $\sigma$ is the stack-history ledger whose entries are finite $\ListUp$
  rows over $\Gamma$;
\item $e$ is the endpoint row of the run ledger;
\item $\chi$ is the acceptance readback row, by final state or by displayed
  empty-stack condition as named in the packet;
\item $H$ stores componentwise $\hsame$ transports for state, input, stack,
  transition, run, stack-history, endpoint, and classifier rows;
\item $C$ stores the $\Cont$ replay routes for reading input symbols,
  stack-top rows, transition entries, and the finite run ledger;
\item $P$ stores the $\Pkg$ provenance naming $\FiniteAutomatonUp$,
  $\RegularLanguageUp$, $\ContextFreeGrammarUp$, $\TuringMachineUp$,
  $\ListUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ stores the local $\NameCert_{\PushdownAutomatonUp}$ rows.
\end{enumerate}
The carrier predicate is $\mathsf{PushdownAutomatonPacket}(A)$. It exports no
host language set, grammar quotient, selected parse tree, infinite branch
choice, or unbounded machine execution.
\end{definition}

\begin{theorem}[PushdownAutomaton NameCert obligations]
\label{thm:pushdown-automaton-namecert-obligations}
For every accepted $\PushdownAutomatonUp$ carrier
$$
A=(Q,\Sigma,\Gamma,\delta,q_0,Z_0,F,w,\rho,\sigma,e,\chi,H,C,P,N),
$$
the local $\NameCert_{\PushdownAutomatonUp}$ surface consists of carrier
admission, finite transition replay, stack-row stability, endpoint classifier
stability, componentwise $\hsame$ transport, $\Cont$ replay, and $\Pkg$
provenance for the rows in
\autoref{def:pushdown-automaton-carrier}. A consumer may project the finite
control, alphabet, stack, transition, input, run, stack-history, endpoint, and
local naming rows, but it obtains no regular-language quotient, context-free
grammar quotient, selected parse tree, or unbounded $\TuringMachineUp$ trace.
\end{theorem}
\begin{proof}
Project the accepted carrier $A$. The rows $Q,\Sigma,\Gamma,\delta,q_0,Z_0,F$
name the finite control and stack presentation, while $w,\rho,\sigma,e,\chi$
name the inspected input, run ledger, stack ledger, endpoint, and acceptance
readback.

Finite transition replay is obtained by reading $\rho$ one displayed step at a
time. Each step consults the current state row, the next consumed input row
when present, the top stack-symbol row, and one transition entry of $\delta$.

The structural rows $H,C,P,N$ transport and replay exactly these coordinates.
Since the carrier has no coordinate for a host language set, grammar quotient,
selected parse tree, or unbounded machine trace, no consumer can extract such
data from the local NameCert surface.
\end{proof}

\begin{theorem}[PushdownAutomaton stack-transition stability]
\label{thm:pushdown-automaton-stack-transition-stability}
Let
$$
A=(Q,\Sigma,\Gamma,\delta,q_0,Z_0,F,w,\rho,\sigma,e,\chi,H,C,P,N)
$$
be an accepted $\PushdownAutomatonUp$ carrier. Every displayed transition step
in $\rho$ transports the current stack row in $\sigma$ to the next stack row
by popping the displayed top symbol and pushing the finite replacement
$\ListUp$ row named by the corresponding transition entry. The transported
step preserves the input cursor, endpoint readback, $\hsame$ rows, $\Cont$
routes, and $\Pkg$ provenance, and it exports no hidden stack contents,
epsilon-closure quotient, or infinite run branch.
\end{theorem}
\begin{proof}
Read one step of the finite run ledger. The step exposes the current control
state, the optional consumed input symbol, the current stack row, and the
top-stack symbol read by the transition entry.

Use the displayed transition entry of $\delta$ to form the next state and the
finite replacement stack word. The next stack ledger entry in $\sigma$ is
obtained by replacing the visible top symbol with that finite $\ListUp$ word
and leaving the unreduced stack suffix as the displayed remainder row.

The componentwise $\hsame$ rows transport the state, input cursor, stack row,
transition entry, and endpoint readback. The $\Cont$ route then passes the
remaining finite run ledger to the next step, and the $\Pkg$ row records the
same finite-recognizer, grammar, and machine-boundary provenance.

No other stack data is available. In particular, the packet contains no
epsilon-closure quotient, selected infinite branch, hidden stack store, or
unbounded machine trace.
\end{proof}

\closureat{PushdownAutomatonUp}{seedStr}

\begin{closurestatus}{\PushdownAutomatonUp}
  \constructivestory{A $\PushdownAutomatonUp$ packet is generated from finite control rows, input alphabet rows, stack alphabet rows, a transition ledger, start and initial-stack rows, accepting rows, a finite input word, a finite run ledger, a stack-history ledger, an endpoint readback, componentwise $\hsame$ transports, $\Cont$ replay routes, $\Pkg$ provenance, and local $\NameCert$ rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:pushdown-automaton-carrier}, \autoref{thm:pushdown-automaton-namecert-obligations}, and \autoref{thm:pushdown-automaton-stack-transition-stability} seed the finite stack-recognizer carrier, local NameCert surface, and stack-transition stability boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, equivalence with all context-free grammars, language-set semantics, determinization, selected parse trees, infinite branch choice, or unbounded Turing-machine recognition.}
  \upgradepath{Obligation closure requires checked carrier admission, transition replay, stack-row stability, acceptance readback, and ledger non-escape for BEDC.Derived.PushdownAutomatonUp.}
\end{closurestatus}
