\chapter{A Concrete Naming Certificate for $\FiniteIntervalChoiceUp$}
\label{ch:concrete-instances-finite-interval-choice-namecert}
\origin{human}

Following Bishop and Bridges on finite choice over displayed finite covers, the $\FiniteIntervalChoiceUp$ packet records the finite selector surface needed when a closed bounded interval net is read through finite stream windows. It sits over the finite mesh route of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}, the observation schedule of \autoref{ch:concrete-instances-finite-stream-namecert}, the stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only choices made inside an already displayed finite row; it does not import countable choice, an ambient selector, trichotomy, quotient real equality, or host compactness.

\begin{definition}[Finite interval choice carrier]
\label{def:finite-interval-choice-carrier}
A $\FiniteIntervalChoiceUp$ carrier is a finite $\BHist$ packet
$$
I=(K,Q,L,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\ClosedBoundedIntervalNetUp$ cell-data row, including the located interval source, finite mesh scale, rational cells, dyadic refinements, center rows, and finite coverage ledger.
\item $Q$ is the $\FiniteStreamUp$ request row that lists exactly the interval-net reads demanded by the consumer.
\item $L$ is the finite $\ListUp$ spine carried by the request row $Q$.
\item $W$ is the $\StreamNameUp$ window row exposed over the same finite request row and list spine.
\item $R$ is the $\RegSeqRatUp$ readback boundary available after $K,Q,L,W$ have been displayed.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row attached to the same interval-net cells and stream windows.
\item $E$ is the downstream $\RealUp$ seal row reached only after the displayed cell, request, window, readback, and tolerance rows.
\item $H$ records componentwise $\hsame$ transport for the interval net, request row, list spine, stream windows, regular readbacks, dyadic tolerances, Real seal, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from an interval-net request through $K,Q,L,W,R,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteIntervalChoiceUp$, $\ClosedBoundedIntervalNetUp$, $\FiniteStreamUp$, $\ListUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteIntervalChoiceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,Q,L,W,R,D,E,H,C,P,N$. No coordinate stores a hidden chooser, countable family of choices, host subcover selector, quotient real equality, trichotomy branch, or ambient completeness principle.
\end{definition}

\begin{theorem}[Finite interval choice NameCert obligations]
\label{thm:finite-interval-choice-namecert-obligations}
For every accepted $\FiniteIntervalChoiceUp$ carrier
$$
I=(K,Q,L,W,R,D,E,H,C,P,N),
$$
the local $\NameCert_{\FiniteIntervalChoiceUp}$ surface consists exactly of carrier admission for the $\ClosedBoundedIntervalNetUp$ cell-data row, the $\FiniteStreamUp$ request row, the finite $\ListUp$ spine, the $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback boundary, the $\DyadicRatCoreUp$ tolerance row, the $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. The finite-choice clause says that each selected interval-net read is indexed by the displayed finite request row $Q$ and list spine $L$. The window clause says that every stream, regular-rational, dyadic, or Real-facing consumer must pass through the same $Q,L,W$ route before reading $R,D,E$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-interval-choice-carrier}. The displayed rows are exactly the interval-net cell data, finite request row, list spine, stream window, regular readback, dyadic tolerance, Real seal, and structural rows $H,C,P,N$.

The finite-choice clause is row exactness. A choice made by the packet is not a host selector; it is the finite coordinate of $Q$ as represented by $L$ and then read by $W$.

The downstream rows preserve that finite coordinate. The readback row $R$, tolerance row $D$, and Real seal $E$ appear only after $K,Q,L,W$, while $H,C,P,N$ transport, replay, source, and name the same route. Hence no countable-choice, subcover-selector, quotient-equality, trichotomy, or ambient-completeness row is available.
\end{proof}

\begin{theorem}[Finite interval choice closed-bounded-net handoff]
\label{thm:finite-interval-choice-closed-bounded-net-handoff}
Every $\RealUp$-facing read accepted by a $\FiniteIntervalChoiceUp$ packet factors through the finite route
$$
K,Q,L,W,R,D,E,H,C,P,N.
$$
Here $K$ supplies the $\ClosedBoundedIntervalNetUp$ cell data, $Q$ and $L$ display the finite request spine, $W$ exposes the corresponding $\StreamNameUp$ windows, $R$ supplies the $\RegSeqRatUp$ readback, $D$ supplies the $\DyadicRatCoreUp$ tolerance ledger, and $E$ supplies the terminal $\RealUp$ seal. The handoff gives L10 interval-net consumers a constructive finite-choice certificate without countable choice, hidden selectors, quotient real equality, or ambient real completeness.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:finite-interval-choice-namecert-obligations}. They bind the interval-net row $K$ to the same finite request row $Q$ and list spine $L$ before any stream window is exposed.

The StreamName, RegSeqRat, DyadicRatCore, and Real rows are then downstream of the same request coordinate. The displayed replay row $C$ prevents a consumer from replacing $Q$ by a sibling request row, and the transport row $H$ preserves equality only componentwise along the displayed packet.

Finally the provenance and local naming rows $P,N$ name the same finite route. Since the carrier has no coordinate for a hidden selector, a countable choice family, quotient real equality, trichotomy, or ambient completeness, the closed-bounded-net handoff is exactly the constructive finite-choice route displayed above.
\end{proof}

\falsifiablePrediction{An accepted $\FiniteIntervalChoiceUp$ read is refuted if it reaches a $\ClosedBoundedIntervalNetUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, or $\RealUp$ consumer without displaying the same finite request row, finite list spine, window row, readback boundary, dyadic tolerance row, Real seal, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ evidence.}

\independenceWitness{closedboundedintervalnet, finite_stream, streamname, regseqrat, dyadicratcore, real: $\FiniteIntervalChoiceUp$ is not bijective to any listed sibling because it binds interval-net cell data to one displayed finite request row and the downstream readback, tolerance, and Real seal rows as a single finite-choice packet.}

\closureat{FiniteIntervalChoiceUp}{seedStr}

\begin{closurestatus}{\FiniteIntervalChoiceUp}
  \constructivestory{A $\FiniteIntervalChoiceUp$ packet is generated from ClosedBoundedIntervalNet cell data, a FiniteStream request row, a finite ListUp spine, StreamName windows, RegSeqRat readbacks, DyadicRatCore tolerances, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-interval-choice-carrier}, \autoref{thm:finite-interval-choice-namecert-obligations}, and \autoref{thm:finite-interval-choice-closed-bounded-net-handoff} seed the finite-choice route for L10 interval-net and finite-stream reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, hidden host selectors, open-cover compactness, quotient real equality, trichotomy, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite request exactness, interval-net handoff, StreamName and RegSeqRat readback exactness, DyadicRatCore tolerance nonescape, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.FiniteIntervalChoiceUp.}
\end{closurestatus}
