\chapter{A Concrete Naming Certificate for $\LocatedRealCauchyCompletenessUp$}
\label{ch:concrete-instances-located-real-cauchy-completeness-namecert}
\origin{human}

Following Bishop and Bridges, located real Cauchy completeness is read constructively as a finite route from located rational interval evidence and regular rational names to a Real-name boundary, not as an ambient selection principle. The $\LocatedRealCauchyCompletenessUp$ packet records this L10 route beside the located-real surface of \autoref{ch:concrete-instances-locatedreal-namecert}, the Cauchy-modulus carrier of \autoref{ch:concrete-instances-cauchy-modulus-space-namecert}, the stream-name observation surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[Located real Cauchy completeness carrier]
\label{def:located-real-cauchy-completeness-carrier}
A $\LocatedRealCauchyCompletenessUp$ carrier is a finite $\BHist$ packet
$$
L=(X,M,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\LocatedRealUp$ admission row, exposing located interval evidence before any completion read is public.
\item $M$ is the $\CauchyModulusSpaceUp$ modulus row that names the displayed Cauchy request and its finite tail budget.
\item $W$ is the $\StreamNameUp$ window row whose finite observations are read by the modulus.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used by the window and modulus rows.
\item $R$ is the $\RegSeqRatUp$ regular rational readback row assembled from $W$ and $D$.
\item $E$ is the terminal $\RealUp$ seal row, available only after located admission, modulus exposure, finite windows, dyadic tolerance, and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for located-real, modulus, stream, dyadic, regular-readback, Real-seal, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from located admission through $X,M,W,D,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\LocatedRealCauchyCompletenessUp$, $\LocatedRealUp$, $\CauchyModulusSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedRealCauchyCompletenessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,M,W,D,R,E,H,C,P,N$. It has no coordinate for quotient real equality, selected limits, countable choice, a host limit operator, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Located real Cauchy completeness NameCert obligations]
\label{thm:located-real-cauchy-completeness-namecert-obligations}
For every accepted $\LocatedRealCauchyCompletenessUp$ carrier
$$
L=(X,M,W,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\LocatedRealCauchyCompletenessUp}$ surface consists exactly of located-real admission for $X$, modulus exposure for $M$, finite StreamName windows for $W$, dyadic tolerance visibility for $D$, RegSeqRat readback for $R$, terminal Real sealing for $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, sibling provenance through $P$, and local naming through $N$.

No located-real Cauchy completeness obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-real-cauchy-completeness-carrier}. The tuple $X,M,W,D,R,E,H,C,P,N$ is the whole public packet, so carrier admission and local naming are exhausted by the displayed rows.

The completion route begins with the located-real row $X$ and the modulus row $M$. The finite StreamName window $W$ is read against the DyadicRatCore tolerance ledger $D$, and the RegSeqRat readback $R$ packages the same finite observations as a regular rational name.

Only after those rows have been displayed may the terminal Real seal $E$ be consumed. The transport, replay, provenance, and local naming rows $H,C,P,N$ preserve the same route and introduce no quotient equality, selected limit, countable-choice schedule, host limit operator, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Located real Cauchy completeness regular readback route]
\label{thm:located-real-cauchy-completeness-regular-readback-route}
Every accepted $\LocatedRealCauchyCompletenessUp$ packet exposes its completion neighbour through the finite route
$$
\LocatedRealUp \longrightarrow \CauchyModulusSpaceUp \longrightarrow \StreamNameUp \longrightarrow \DyadicRatCoreUp \longrightarrow \RegSeqRatUp \longrightarrow \RealUp .
$$
The $\RegSeqRatUp$ row is therefore the regular readback boundary between located interval evidence and the terminal Real seal. The route does not export quotient real equality, selected limits, countable choice, a host limit operator, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the located-real row $X$ first. It supplies the located interval evidence that anchors the Cauchy request without identifying host real values.

Next read the modulus row $M$ and the finite StreamName window row $W$. The DyadicRatCore ledger $D$ supplies the tolerance scale shared by both rows.

The RegSeqRat row $R$ is then the only regular rational readback available to the packet. The terminal Real seal $E$ is downstream of $R$, and $H,C,P,N$ merely transport, replay, source, and name the same finite evidence.

Since the carrier has no quotient-real, selected-limit, countable-choice, host-limit, or ambient-completeness coordinate, every completion read remains inside the displayed regular readback route.
\end{proof}

\closureat{LocatedRealCauchyCompletenessUp}{seedStr}

\begin{closurestatus}{\LocatedRealCauchyCompletenessUp}
  \constructivestory{A $\LocatedRealCauchyCompletenessUp$ packet is generated from located-real admission, CauchyModulusSpace modulus exposure, finite StreamName windows, DyadicRatCore tolerances, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-real-cauchy-completeness-carrier}, \autoref{thm:located-real-cauchy-completeness-namecert-obligations}, and \autoref{thm:located-real-cauchy-completeness-regular-readback-route} seed the finite located-real Cauchy completeness route from located admission through regular rational readback to a terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient real equality, selected limits, countable choice, host limit operators, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked located-real admission, modulus exposure, finite-window coverage, dyadic tolerance visibility, RegSeqRat readback, Real seal routing, transport stability, replay stability, and non-escape for BEDC.Derived.LocatedRealCauchyCompletenessUp.}
\end{closurestatus}
