\chapter{A Concrete Naming Certificate for $\PhaseDistanceObserverExpansionUp$}
\label{ch:concrete-instances-phase-distance-observer-expansion-namecert}
\origin{ai}

The $\PhaseDistanceObserverExpansionUp$ packet realizes the phase-distance observer-expansion reading of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite NameCert data. It sits between the visual-shadow metric route of \autoref{ch:concrete-instances-hyperbolic-visual-shadow-metric-namecert}, the boundary-shadow route of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, the focused expansion ledger of \autoref{ch:concrete-instances-hyperbolic-expansion-ledger-namecert}, the observer-expansion certificate of \autoref{ch:concrete-instances-hyperbolic-observer-expansion-namecert}, and the observer-shell packet of \autoref{ch:concrete-instances-hyperbolic-observer-shell-namecert}. The packet names one finite observer-phase and distance-comparison surface; it is not a host hyperbolic space, a physical cosmology, a global clock, or a completed observer trajectory.

\falsifiablePrediction{Every accepted $\PhaseDistanceObserverExpansionUp$ consumer must expose observer-phase rows, distance-read rows, expansion-comparison rows, provenance rows, hsame transport, Cont replay, Pkg support, and local NameCert data before it exports a phase-distance expansion judgment.}

\independenceWitness{hyperbolic-visual-shadow-metric, hyperbolic-boundary-shadow, hyperbolic-expansion-ledger, hyperbolic-observer-expansion, hyperbolic-observer-shell: the visual-shadow metric supplies distance comparison without observer-phase provenance; the boundary-shadow packet supplies boundary routing without expansion comparison; the expansion ledger records growth without phase-distance readback; the observer-expansion packet records shadow expansion without this phase-distance comparison surface; and the observer shell packages surrounding routes without identifying this local carrier.}

\begin{definition}[PhaseDistanceObserverExpansion carrier]
\label{def:phase-distance-observer-expansion-carrier}
A $\PhaseDistanceObserverExpansionUp$ carrier is a finite $\BHist$ packet
$$
Q=(O,\Phi,D,E,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the observer-window row, recording the focused history, visible disk window, and local observation budget inspected by the packet.
\item $\Phi$ is the observer-phase row, read through phase-ledger and disk-coordinate data rather than through a hidden global phase.
\item $D$ is the distance-read row, recording the displayed metric, visual-shadow, or boundary-shadow comparison used by the local read.
\item $E$ is the expansion-comparison row, saying which earlier and later observer windows are compared and how the displayed distance-read changes along the local $\Cont$ route.
\item $B$ is the boundary and refusal row, recording that the expansion is a records-side readback and not a physical cosmology, global clock, host hyperbolic model, or completed observer trajectory.
\item $H$ records componentwise $\hsame$ transport for observer-window, phase, distance, expansion, boundary-refusal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from an observer-window request through
$$
O,\Phi,D,E,B \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\PhaseDistanceObserverExpansionUp$, $\HyperbolicVisualShadowMetricUp$, $\HyperbolicBoundaryShadowUp$, $\HyperbolicExpansionLedgerUp$, $\HyperbolicObserverExpansionUp$, $\HyperbolicObserverShellUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PhaseDistanceObserverExpansionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host hyperbolic manifold, a global observer, a universal time coordinate, a physical expansion constant, quotient equality of observer histories, or an unlogged boundary completion.
\end{definition}

\begin{theorem}[PhaseDistanceObserverExpansion NameCert obligations]
\label{thm:phase-distance-observer-expansion-namecert-obligations}
For every accepted $\PhaseDistanceObserverExpansionUp$ carrier
$$
Q=(O,\Phi,D,E,B,H,C,P,N),
$$
the local $\NameCert_{\PhaseDistanceObserverExpansionUp}$ surface consists exactly of observer-window admission, observer-phase admission, distance-read admission, expansion-comparison admission, boundary-refusal coverage, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. No NameCert obligation is stored outside $O,\Phi,D,E,B,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:phase-distance-observer-expansion-carrier}. The only public rows are the observer window, observer phase, distance read, expansion comparison, boundary refusal, transport, replay, provenance, and local name rows.

Rows $O$ and $\Phi$ fix the observer-side and phase-side data. The phase read is therefore tied to a focused finite ledger rather than to an unlogged global phase surface.

Rows $D$ and $E$ supply the comparison. The distance read is the displayed metric or visual-shadow row, and the expansion row records the before-and-after comparison along a local $\Cont$ route.

Row $B$ keeps the packet at the representation layer by refusing host hyperbolic geometry, physical cosmology, global clocks, and completed observer trajectories. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite route, so the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[PhaseDistanceObserverExpansion comparison handoff]
\label{thm:phase-distance-observer-expansion-comparison-handoff}
Every phase-distance expansion read from an accepted $\PhaseDistanceObserverExpansionUp$ packet factors through
$$
O,\Phi,D,E,B \longmapsto H,C,P,N .
$$
The handoff exports a finite observer-phase, distance-read, and expansion-comparison certificate, not an ambient hyperbolic model, physical expansion law, global observer, or completed boundary object.
\end{theorem}
\begin{proof}
Use the obligations of \autoref{thm:phase-distance-observer-expansion-namecert-obligations}. An expansion consumer first receives the observer-window and phase rows.

The distance row and expansion-comparison row then determine what can be compared. Since both are displayed rows of the carrier, the comparison remains local to the inspected observer-window route.

The refusal row blocks readings that require a host hyperbolic model, a physical cosmology, a global clock, or completed observer trajectory. Transport, replay, provenance, and naming only preserve that finite packet, so the handoff exports exactly the listed finite comparison surface.
\end{proof}

\closureat{PhaseDistanceObserverExpansionUp}{seedStr}

\begin{closurestatus}{\PhaseDistanceObserverExpansionUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:phase-distance-observer-expansion-carrier}, \autoref{thm:phase-distance-observer-expansion-namecert-obligations}, and \autoref{thm:phase-distance-observer-expansion-comparison-handoff} seed the phase-distance observer-expansion carrier, local obligation surface, and comparison handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host hyperbolic geometry, physical cosmology, global observers, universal clocks, quotient observer-history equality, completed boundary objects, Lean verification, or bridge checking.}
  \upgradepath{Formal verification can encode observer-window admission, phase admission, distance-read admission, expansion-comparison admission, boundary-refusal coverage, transport, replay, provenance, and local naming for BEDC.Derived.PhaseDistanceObserverExpansionUp.}
  \constructivestory{A $\PhaseDistanceObserverExpansionUp$ packet is generated from observer-window, observer-phase, distance-read, expansion-comparison, boundary-refusal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
\end{closurestatus}
