\chapter{A Concrete Naming Certificate for $\BaireCategoryCompleteMetricUp$}
\label{ch:concrete-instances-baire-category-complete-metric-namecert}
\origin{human}

Following Bishop and Oxtoby, the $\BaireCategoryCompleteMetricUp$ packet records the complete-metric dense-open intersection route as finite NameCert data rather than as an ambient theorem about all complete metric spaces. It sits over the dense-open schedule of \autoref{ch:concrete-instances-bairecategory-namecert}, the complete-metric source of \autoref{ch:concrete-instances-completemetric-namecert}, the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[BaireCategoryCompleteMetric carrier]
\label{def:baire-category-complete-metric-carrier}
A $\BaireCategoryCompleteMetricUp$ carrier is a finite $\BHist$ packet
$$
Q=(B,K,M,D,S,R,Y,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\BaireCategoryUp$ dense-open schedule row, listing the finite dense-open requests and the predecessor-ball refinements visible to the packet.
\item $K$ is the $\CompleteMetricUp$ source row, exposing the displayed Cauchy-thread service and limit handoff used by the dense-open route.
\item $M$ is the $\MetricUp$ carrier row, naming the finite distance, ball, and comparison observations consumed by $B$ and $K$.
\item $D$ is the dense-open schedule ledger, recording the finite list of open rows, density witnesses, successor-ball choices, and requested indices.
\item $S$ is the $\StreamNameUp$ finite-window row through which the schedule, centers, radii, and requested tolerances are inspected.
\item $R$ is the $\RegSeqRatUp$ readback row for the rational center and radius data visible before the terminal seal.
\item $Y$ is the $\DyadicRatCoreUp$ tolerance ledger, storing the displayed dyadic radii and shrinkage comparisons used by the regular rational readback.
\item $E$ is the $\RealUp$ seal reached only after the dense-open schedule, complete-metric source, metric carrier, finite windows, regular-rational readback, and dyadic tolerance ledger have been displayed.
\item $H$ records componentwise $\hsame$ transport for the dense-open schedule, complete-metric source, metric carrier, stream windows, regular-rational readback, dyadic tolerance ledger, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the same dense-open, complete-metric, metric, window, readback, tolerance, and seal route.
\item $P$ is the $\Pkg$ provenance over $\BaireCategoryCompleteMetricUp$, $\BaireCategoryUp$, $\CompleteMetricUp$, $\MetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BaireCategoryCompleteMetricUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $B,K,M,D,S,R,Y,E,H,C,P,N$. It has no coordinate for countable choice, a host intersection, an open-cover compactness theorem, a selected limit point, ambient $\RealUp$ completeness, or a standard bridge datum.
\end{definition}

\begin{theorem}[BaireCategoryCompleteMetric NameCert obligations]
\label{thm:baire-category-complete-metric-namecert-obligations}
For every accepted $\BaireCategoryCompleteMetricUp$ carrier
$$
Q=(B,K,M,D,S,R,Y,E,H,C,P,N),
$$
the local $\NameCert_{\BaireCategoryCompleteMetricUp}$ surface exposes exactly the dense-open schedule rows, complete-metric source row, metric carrier row, finite $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming row. Every complete-metric Baire read is routed through those rows, and no obligation is stored outside them.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:baire-category-complete-metric-carrier}. The rows $B,K,M,D,S,R,Y,E$ are the only analytic rows available to a consumer: Baire schedule, complete-metric service, metric comparison, dense-open ledger, finite windows, regular rational readback, dyadic tolerances, and terminal real seal.

The dense-open content is read first through $B$ and $D$. Each request exposes only finite open rows, density witnesses, and successor-ball choices; the complete-metric row $K$ then carries the displayed Cauchy thread built from those finite refinements.

The metric and numerical observations are constrained by $M,S,R,Y,E$. The metric carrier supplies distance and ball comparisons, the stream row supplies finite inspection windows, the dyadic ledger supplies radius comparisons, the regular-rational row reads center and radius data, and the real seal is reached only after those rows have been displayed.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier contains no coordinate for countable choice, host intersections, open-cover compactness, selected limit points, ambient real completeness, or bridge data, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[BaireCategoryCompleteMetric dense-open handoff]
\label{thm:baire-category-complete-metric-dense-open-handoff}
Let $Q=(B,K,M,D,S,R,Y,E,H,C,P,N)$ be an accepted $\BaireCategoryCompleteMetricUp$ carrier. Any downstream constructive Baire-category or Banach-style consumer that reads a dense-open intersection through a complete metric source must read the $\BaireCategoryUp$ schedule $B$, dense-open ledger $D$, $\CompleteMetricUp$ source $K$, $\MetricUp$ carrier $M$, $\StreamNameUp$ finite windows $S$, $\RegSeqRatUp$ readback $R$, $\DyadicRatCoreUp$ tolerance ledger $Y$, and $\RealUp$ seal $E$, transported and replayed only by $H,C,P,N$.

The handoff exports no countable-choice selector, host intersection, selected limit point, open-cover compactness theorem, ambient $\RealUp$ completeness theorem, or additional completion carrier.
\end{theorem}
\begin{proof}
Start with the dense-open rows $B$ and $D$. They display the finite schedule and successor-ball refinements already present in the packet, so a consumer cannot replace them by an external countable family or host intersection.

Next read the complete-metric and metric rows $K$ and $M$. The complete-metric source supplies only the Cauchy-thread service recorded in the packet, while the metric carrier supplies the finite distance and ball comparisons used by that thread.

Route the numerical part through $S,R,Y,E$. The stream windows expose the requested finite observations, the dyadic ledger records the tolerance shrinkage, the regular-rational readback carries the displayed center and radius data, and the terminal real seal is reached only from those finite rows.

The structural rows $H,C,P,N$ preserve the same route under transport, replay, provenance, and local naming. Coordinate exhaustion then gives the stated handoff boundary: every downstream consumer receives the displayed finite packet and nothing beyond it.
\end{proof}

\closureat{BaireCategoryCompleteMetricUp}{seedStr}

\begin{closurestatus}{\BaireCategoryCompleteMetricUp}
  \constructivestory{A $\BaireCategoryCompleteMetricUp$ packet is generated from a BaireCategory dense-open schedule, a CompleteMetric source row, a Metric carrier row, finite StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:baire-category-complete-metric-carrier}, \autoref{thm:baire-category-complete-metric-namecert-obligations}, and \autoref{thm:baire-category-complete-metric-dense-open-handoff} seed the complete-metric dense-open intersection packet over the displayed finite rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close countable choice, host intersections, open-cover compactness, selected limit points, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-open schedule exposure, complete-metric source exactness, metric row compatibility, finite-window readback, dyadic tolerance exactness, regular-rational readback, real sealing, and nonescape for BEDC.Derived.BaireCategoryCompleteMetricUp.}
\end{closurestatus}
