\chapter{A Concrete Naming Certificate for $\CauchyCondensationTailLockUp$}
\label{ch:concrete-instances-cauchy-condensation-tail-lock-namecert}
\origin{human}

Following Cauchy's condensation test and Bishop--Bridges constructive analysis, the $\CauchyCondensationTailLockUp$ packet records the finite tail route by which condensation evidence reaches a regular rational readback and then the Real seal. It consumes the dyadic-block condensation carrier of \autoref{ch:concrete-instances-cauchycondensation-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance surface of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal Real boundary of \autoref{ch:concrete-instances-real-namecert}. The certificate locks a displayed condensation tail to one completion-facing route; it does not import selected sums, quotient series equality, countable choice, host real equality, or $\RealUp$ completeness.

\begin{definition}[Cauchy condensation tail-lock carrier]
\label{def:cauchy-condensation-tail-lock-carrier}
A $\CauchyCondensationTailLockUp$ carrier is a finite $\BHist$ packet
$$
Q=(S,W,B,L,T,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the monotone nonnegative $\SeriesUp$ source whose finite summand windows are consumed by the condensation route.
\item $W$ is the summand-window ledger inherited from the accepted $\CauchyCondensationUp$ carrier.
\item $B$ is the dyadic block schedule, including displayed block endpoints, powers of two, and block lengths.
\item $L$ is the block-sum ledger, storing the original block sums and the condensed dyadic terms on the same schedule.
\item $T$ is the tail-bound row, recording the dyadic tolerances and finite domination comparisons read through $\DyadicRatCoreUp$.
\item $R$ is the $\RegSeqRatUp$ handoff row produced from $S,W,B,L,T$.
\item $E$ is the $\RealUp$ seal boundary attached to the handoff row $R$.
\item $H$ records componentwise $\hsame$ transports for the source, windows, schedule, block sums, tail bounds, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each finite precision request through $S,W,B,L,T,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\SeriesUp$, $\CauchyCondensationUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyCondensationTailLockUp}$ row.
\end{enumerate}
The classifier compares accepted tail-lock packets only through these rows. It has no coordinate for quotient series equality, a selected infinite sum, countable choice, trichotomy beyond displayed windows, host real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy condensation tail-lock NameCert obligations]
\label{thm:cauchy-condensation-tail-lock-namecert-obligations}
For every accepted $\CauchyCondensationTailLockUp$ carrier $Q=(S,W,B,L,T,R,E,H,C,P,N)$, the local $\NameCert_{\CauchyCondensationTailLockUp}$ surface consists exactly of source exposure for $S$, summand-window coverage for $W$, dyadic block scheduling for $B$, block-sum ledger exposure for $L$, dyadic tail-bound visibility for $T$, $\RegSeqRatUp$ handoff exposure for $R$, $\RealUp$ seal routing for $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, sibling provenance through $P$, and local naming through $N$.

No tail-lock obligation is stored outside the displayed finite packet.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:cauchy-condensation-tail-lock-carrier}. The tuple $S,W,B,L,T,R,E,H,C,P,N$ is the whole public packet, so carrier admission and local naming are exactly the displayed rows.

The analytic route begins with the finite condensation surface of \autoref{ch:concrete-instances-cauchycondensation-namecert}. The source row $S$, summand windows $W$, dyadic schedule $B$, and block ledger $L$ determine which finite terms can be inspected.

The tail-bound row $T$ reads its dyadic tolerances through the $\DyadicRatCoreUp$ surface and sends the resulting finite comparison to the $\RegSeqRatUp$ handoff row $R$. The seal row $E$ is downstream of that handoff.

Transport, replay, provenance, and local naming through $H,C,P,N$ preserve the same route. Since the carrier has no further coordinate, the listed rows exhaust the local certificate.
\end{proof}

\begin{theorem}[Cauchy condensation tail-lock Real-seal route]
\label{thm:cauchy-condensation-tail-lock-real-seal-route}
Every accepted $\CauchyCondensationTailLockUp$ carrier routes a condensation tail to a $\RealUp$ seal only through the finite path
$$
S,W,B,L,T \longmapsto R \longmapsto E.
$$
The route is locked to the same $\RegSeqRatUp$ handoff row before the Real seal is read. No selected sum, quotient series equality, countable choice, trichotomy premise, host real equality, or $\RealUp$ completeness coordinate can produce a second seal-facing path.
\end{theorem}
\begin{proof}
Start with an accepted tail-lock carrier and read the rows exposed by \autoref{thm:cauchy-condensation-tail-lock-namecert-obligations}. The only analytic input available before the handoff is the finite source-window, dyadic-schedule, block-ledger, and tail-bound data $S,W,B,L,T$.

Apply the condensation handoff route of \autoref{thm:cauchy-condensation-dyadic-block-handoff}. It forces the condensation comparison through the displayed dyadic-block surface before any regular rational readback can be consumed.

Now read the Real seal boundary using \autoref{thm:cauchy-condensation-real-seal-nonescape}. The seal-facing input is the handoff row $R$ together with the structural rows $H,C,P,N$, so $E$ cannot be reached by an alternate quotient, selected-sum, choice, trichotomy, host-equality, or completeness coordinate.
\end{proof}

\falsifiablePrediction{An accepted $\CauchyCondensationTailLockUp$ consumer that reaches a $\RealUp$ seal without first reading the displayed rows $S,W,B,L,T$ and the $\RegSeqRatUp$ handoff row $R$ refutes the carrier surface.}

\independenceWitness{cauchycondensation, regseqrat, dyadicratcore, real: no listed sibling supplies the whole tail-lock packet $Q=(S,W,B,L,T,R,E,H,C,P,N)$, because the siblings expose the condensation carrier, regular rational readback, dyadic tolerance surface, or seal boundary separately while this chapter binds them into one finite route.}

\closureat{$\CauchyCondensationTailLockUp$}{seedStr}

\begin{closurestatus}{\CauchyCondensationTailLockUp}
  \constructivestory{A $\CauchyCondensationTailLockUp$ packet is generated from a Series source, condensation windows, dyadic block schedule, block-sum ledger, dyadic tail-bound row, RegSeqRat handoff, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-condensation-tail-lock-carrier}, \autoref{thm:cauchy-condensation-tail-lock-namecert-obligations}, and \autoref{thm:cauchy-condensation-tail-lock-real-seal-route} seed the finite tail-lock route from condensation evidence through dyadic tolerance and RegSeqRat readback to a RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected sums, quotient series equality, countable choice, trichotomy, host real equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked source exposure, summand-window coverage, dyadic block scheduling, block-sum ledger exposure, dyadic tail-bound visibility, RegSeqRat handoff exposure, Real seal routing, transport stability, replay stability, and non-escape for BEDC.Derived.CauchyCondensationTailLockUp.}
\end{closurestatus}
