\chapter{A Concrete Naming Certificate for $\YoungMeasureUp$}
\label{ch:concrete-instances-young-measure-namecert}
\origin{human}

Following Young and standard weak-convergence treatments, the $\YoungMeasureUp$ packet records parametrized limiting probability data as finite BEDC NameCert rows rather than as a quotient measure class or a selected subsequential limit. It sits after the terminal real-name surface of \autoref{ch:concrete-instances-real-namecert}, the probability-space carrier of \autoref{ch:concrete-instances-probspace-namecert}, the tight probability route of \autoref{ch:concrete-instances-prokhorov-tight-probability-namecert}, and the regular-Cauchy completion lattice of \autoref{ch:concrete-instances-regular-cauchy-completion-envelope-namecert}. The packet gives Phase Real and Completion consumers a displayed interface for tight probability and real-sequence limiting data without asserting ambient $\RealUp$ completeness.

\begin{definition}[YoungMeasure carrier]
\label{def:young-measure-carrier}
A $\YoungMeasureUp$ carrier is a finite $\BHist$ packet
$$
Y=(R,P,T,S,Q,E,H,C,K,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUp$ endpoint and observable-value row through which scalar test reads are sealed.
\item $P$ is the $\ProbSpaceUp$ source row naming the probability carrier, measurable event ledger, and finite probability observations.
\item $T$ is the tightness row, read through the Prokhorov-style tight probability packet before any limiting probability read is admitted.
\item $S$ is the real-sequence window row, recording the finite schedule of observations whose limiting behavior the packet exposes.
\item $Q$ is the regular-Cauchy readback row tying the displayed scalar observations to the completion-facing regular rational route.
\item $E$ is the Young-measure evaluation row, recording only test-observable probability reads over displayed windows and tightness ledgers.
\item $H$ records componentwise $\hsame$ transport for real, probability, tightness, sequence-window, regular-readback, evaluation, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a test-observable request through real endpoints, probability rows, tightness rows, sequence windows, regular readback, and evaluation.
\item $K$ is the $\Pkg$ provenance over $\YoungMeasureUp$, $\RealUp$, $\ProbSpaceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ together with the cited tightness and regular-Cauchy dependency rows.
\item $N$ is the local $\NameCert_{\YoungMeasureUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,P,T,S,Q,E,H,C,K,N$. It has no coordinate for quotient measure equality, selected subsequences, selected host limits, countable choice, arbitrary weak-star compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[YoungMeasure NameCert obligations]
\label{thm:young-measure-namecert-obligations}
For every accepted $\YoungMeasureUp$ carrier
$$
Y=(R,P,T,S,Q,E,H,C,K,N),
$$
the local $\NameCert_{\YoungMeasureUp}$ surface consists exactly of Real endpoint exposure, probability-source exposure, tightness exposure, real-sequence window exposure, regular-Cauchy readback, Young-measure evaluation exposure, componentwise transport, displayed replay, package provenance, and local naming. No obligation is stored outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:young-measure-carrier}. The displayed coordinates are precisely the Real endpoint row, probability source row, tightness row, sequence-window row, regular-readback row, evaluation row, and structural rows.

The probability and tightness obligations are read from $P$ and $T$. Thus an accepted packet exposes tight limiting data only after the probability carrier and its tightness ledger have been displayed.

The real-valued observation obligations are read from $R,S,Q,E$. The sequence window $S$ and regular readback $Q$ keep scalar limiting data in the finite completion corridor before the evaluation row $E$ is presented.

Finally $H,C,K,N$ transport, replay, source, and name the same route. Since no quotient measure equality, selected subsequence, selected limit, countable-choice schedule, weak-star compactness theorem, or ambient completeness row appears in the carrier, none can be exported by the local NameCert surface.
\end{proof}

\begin{theorem}[YoungMeasure tightness handoff]
\label{thm:young-measure-tightness-handoff}
Every tight probability read accepted by a $\YoungMeasureUp$ carrier factors through the displayed probability source row, tightness row, finite real-sequence windows, regular-Cauchy readback, and local structural rows before any evaluation row is visible. The route is
$$
P,T,S,Q \longmapsto R,E \longmapsto H,C,K,N .
$$
It exports a finite tightness handoff for probability-valued limiting data, not a quotient measure equality, a selected subsequence, or a host compactness principle.
\end{theorem}
\begin{proof}
Use the obligation theorem \autoref{thm:young-measure-namecert-obligations}. It exposes the probability source and tightness rows before the sequence-window and regular-readback rows can be inspected by a limiting-data consumer.

The evaluation row is downstream of those finite rows. A consumer reaches $E$ only after the probability source $P$, tightness ledger $T$, sequence window $S$, regular readback $Q$, and Real endpoint row $R$ have been displayed.

The structural rows then preserve the same handoff. Componentwise transport $H$, replay $C$, provenance $K$, and local naming $N$ cannot add quotient measure equality, selected subsequences, or host compactness, because those are not carrier coordinates.
\end{proof}

\begin{theorem}[YoungMeasure Real completion boundary]
\label{thm:young-measure-real-completion-boundary}
No $\RealUp$-facing completion consumer of an accepted $\YoungMeasureUp$ carrier can bypass the displayed route through Real endpoints, probability-source rows, tightness ledgers, real-sequence windows, regular-Cauchy readbacks, evaluation rows, and local structural rows. In particular, the packet does not assert quotient measure equality, selected limits, selected subsequences, countable choice, arbitrary weak convergence, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the carrier projection of \autoref{def:young-measure-carrier}. The only Real-facing row is $R$, and the only completion-facing scalar readback row is $Q$.

Apply the tightness handoff \autoref{thm:young-measure-tightness-handoff}. It places the probability source and tightness ledger before the sequence-window, regular-readback, and evaluation rows.

The Real endpoint row is therefore a boundary for displayed scalar observations, not a completeness theorem. Since the carrier stores no quotient measure equality, selected limit, selected subsequence, countable-choice schedule, arbitrary weak-convergence theorem, or ambient completeness row, a completion consumer cannot obtain any of those principles from the packet.
\end{proof}

\closureat{YoungMeasureUp}{seedStr}

\begin{closurestatus}{\YoungMeasureUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:young-measure-carrier}, \autoref{thm:young-measure-namecert-obligations}, \autoref{thm:young-measure-tightness-handoff}, and \autoref{thm:young-measure-real-completion-boundary} seed the finite Young-measure carrier, local obligation surface, tightness handoff, and Real-completion boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient measure equality, selected subsequences, selected host limits, countable choice, arbitrary weak-star compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Formal verification can encode carrier admission, probability-source exposure, tightness handoff, sequence-window readback, Real endpoint boundary, transport, replay, provenance, and local naming for BEDC.Derived.YoungMeasureUp.}
  \constructivestory{A $\YoungMeasureUp$ packet is generated from Real endpoint rows, probability-source rows, tightness rows, real-sequence windows, regular-Cauchy readbacks, Young-measure evaluation rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
\end{closurestatus}
