\chapter{A Concrete Naming Certificate for $\FiniteWindowMetaCICDiamondEnvelopeUp$}
\label{ch:concrete-instances-finite-window-metacic-diamond-envelope-namecert}
\origin{ai}

The $\FiniteWindowMetaCICDiamondEnvelopeUp$ packet realizes the confluence audit map of \autoref{ch:metacic-confluence-audit-map} as a finite residual-window diamond envelope. It sits beside the residual-substitution boundary of \autoref{ch:concrete-instances-metacic-residual-substitution-boundary-namecert}, the parallel-diamond frontier of \autoref{ch:concrete-instances-metacic-parallel-diamond-frontier-namecert}, the residual-join determinacy packet of \autoref{ch:concrete-instances-metacic-residual-join-determinacy-namecert}, and the closed parallel-diamond premise ledger of \autoref{ch:concrete-instances-closed-parallel-diamond-premise-ledger-namecert}. The packet records bounded peak, residual-window, candidate-join, premise-retention, and TasteGate-readiness rows without claiming residual-substitution compatibility, a premise-free parallel diamond, arbitrary closed Church--Rosser, subject reduction, evaluator equality, quotient conversion equality, or kernel consistency.

\falsifiablePrediction{A $\FiniteWindowMetaCICDiamondEnvelopeUp$ read is rejected whenever its residual-window row is present but either the residual-substitution boundary row or the closed parallel-diamond premise ledger row is absent.}

\independenceWitness{metacic-residual-substitution-boundary, metacic-parallel-diamond-frontier, metacic-residual-join-determinacy, closed-parallel-diamond-premise-ledger: $\FiniteWindowMetaCICDiamondEnvelopeUp$ is not bijective to any listed sibling because it jointly carries a bounded peak window, residual-window budget, candidate-join determinacy, parallel-diamond frontier handoff, closed-premise ledger, obstruction-retention row, TasteGate-readiness row, transport, replay, provenance, and local NameCert data.}

\begin{definition}[Finite-window MetaCIC diamond-envelope carrier]
\label{def:finite-window-metacic-diamond-envelope-carrier}
A $\FiniteWindowMetaCICDiamondEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(W,R,J,F,L,O,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the bounded MetaCIC peak-window row, naming the source term, two parallel observations, and the finite residual radius.
\item $R$ is the $\MetaCICResidualSubstitutionBoundaryUp$ row, kept visible as the residual-substitution premise boundary for the same peak.
\item $J$ is the $\MetaCICResidualJoinDeterminacyUp$ row, recording the budgeted local-join candidate and determinacy readback for the residual window.
\item $F$ is the $\MetaCICParallelDiamondFrontierUp$ row, exposing the conditional parallel-diamond frontier consumed by the envelope.
\item $L$ is the $\ClosedParallelDiamondPremiseLedgerUp$ row, recording the closed-premise ledger that any closed-star handoff must cite.
\item $O$ is the obstruction-retention row, stating that the envelope still displays the missing residual-substitution premise whenever the conditional frontier is read.
\item $G$ is the $\TasteGate$ readiness row for later $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances over the displayed envelope.
\item $H$ records componentwise $\hsame$ transport for peak windows, residual-substitution boundaries, residual joins, frontier rows, closed-premise ledgers, obstruction retention, TasteGate readiness, replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a confluence-audit query through $W,R,J,F,L,O,G,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteWindowMetaCICDiamondEnvelopeUp$, $\MetaCICResidualSubstitutionBoundaryUp$, $\MetaCICResidualJoinDeterminacyUp$, $\MetaCICParallelDiamondFrontierUp$, $\ClosedParallelDiamondPremiseLedgerUp$, $\BHist$, $\hsame$, $\Cont$, $\TasteGate$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteWindowMetaCICDiamondEnvelopeUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through the displayed rows $W,R,J,F,L,O,G,H,C,P,N$. It contains no coordinate for full residual-substitution compatibility, a premise-free parallel diamond, arbitrary closed Church--Rosser, subject reduction, evaluator equality, quotient conversion equality, selected joins, or kernel consistency.
\end{definition}

\begin{theorem}[Finite-window MetaCIC diamond-envelope NameCert obligations]
\label{thm:finite-window-metacic-diamond-envelope-namecert-obligations}
For every accepted $\FiniteWindowMetaCICDiamondEnvelopeUp$ carrier
$$
E=(W,R,J,F,L,O,G,H,C,P,N),
$$
the local $\NameCert_{\FiniteWindowMetaCICDiamondEnvelopeUp}$ surface consists exactly of bounded peak-window exposure through $W$, residual-substitution boundary retention through $R$, residual-join determinacy through $J$, parallel-diamond frontier handoff through $F$, closed-premise ledger exposure through $L$, obstruction retention through $O$, TasteGate readiness through $G$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-metacic-diamond-envelope-carrier}. Rows $W,R,J,F,L,O$ are the confluence-facing envelope data, while $G,H,C,P,N$ are the structural certificate data.

The residual-window read starts with $W$ and $R$. The peak, radius, and two outgoing observations are bounded by $W$, and the residual-substitution boundary row $R$ keeps the missing compatibility premise visible before any diamond-facing handoff can be consumed.

The join and frontier rows are then read through $J,F,L$. The residual-join determinacy row records a budgeted candidate join, the frontier row exposes only the conditional parallel-diamond route, and the closed-premise ledger records the closed handoff that such a route would consume.

The obstruction and structural rows finish the surface. Row $O$ prevents the envelope from being read as a solved residual-substitution theorem, and $G,H,C,P,N$ reserve the TasteGate instance surface, transport the rows, replay the audit query, source the packet, and name it. Since no carrier coordinate contains unrestricted confluence, subject reduction, evaluator equality, quotient conversion equality, selected joins, or kernel consistency, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Finite-window MetaCIC diamond-envelope handoff]
\label{thm:finite-window-metacic-diamond-envelope-handoff}
Every confluence-audit consumer of an accepted $\FiniteWindowMetaCICDiamondEnvelopeUp$ carrier factors through
$$
W,R,J,F,L,O,G,H,C,P,N .
$$
The consumer may inspect the bounded peak window, residual-substitution boundary, residual-join determinacy row, parallel-diamond frontier, closed-premise ledger, obstruction-retention row, TasteGate readiness, transport, replay, provenance, and local name. It cannot bypass this route to obtain full residual-substitution compatibility, a premise-free parallel diamond, arbitrary closed Church--Rosser, subject reduction, evaluator equality, quotient conversion equality, selected joins, or kernel consistency.
\end{theorem}
\begin{proof}
Start with a confluence-audit query. The only entrance to the envelope is the finite peak-window row $W$, and the only residual-substitution premise surface is $R$.

The local join route is constrained by $J$. It records a budgeted candidate join for the displayed residual window, so the consumer may not detach the join row into a global diamond theorem.

The frontier and closed-premise route is constrained by $F$ and $L$. These rows expose the conditional parallel-diamond frontier and the closed parallel-diamond premise ledger, but they do not supply the missing residual-substitution compatibility proof.

Finally $O,G,H,C,P,N$ preserve the same boundary under obstruction retention, TasteGate readiness, transport, replay, provenance, and local naming. Every confluence-audit consumer therefore remains inside the finite envelope route.
\end{proof}

\begin{theorem}[Finite-window MetaCIC diamond-envelope subject slice]
\label{thm:finite-window-metacic-diamond-envelope-subject-slice}
Any subject-reduction-facing consumer of an accepted $\FiniteWindowMetaCICDiamondEnvelopeUp$ packet may inspect only the bounded peak window $W$, residual-substitution boundary $R$, residual-join determinacy row $J$, parallel-diamond frontier $F$, closed-premise ledger $L$, and obstruction-retention row $O$ before reaching TasteGate, transport, replay, provenance, and local naming rows. It cannot turn the envelope into subject reduction, evaluator equality, quotient conversion equality, or kernel consistency.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-metacic-diamond-envelope-carrier}. The subject-facing entrance is still the finite envelope tuple, so the only confluence data visible before the structural rows are $W,R,J,F,L,O$.

Apply \autoref{thm:finite-window-metacic-diamond-envelope-namecert-obligations}. The obligation surface assigns bounded peak exposure to $W$, residual-substitution boundary retention to $R$, residual-join determinacy to $J$, parallel-diamond frontier handoff to $F$, closed-premise ledger exposure to $L$, and obstruction retention to $O$.

Finally use \autoref{thm:finite-window-metacic-diamond-envelope-handoff}. The handoff already blocks full residual-substitution compatibility, premise-free diamonds, subject reduction, evaluator equality, quotient conversion equality, selected joins, and kernel consistency. The present statement records the subject-reduction slice of that boundary; it is not itself a confluence or subject-reduction theorem.
\end{proof}

\begin{theorem}[Finite-window MetaCIC diamond-envelope TasteGate scope]
\label{thm:finite-window-metacic-diamond-envelope-tastegate-scope}
The later Lean side must provide $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ $\TasteGate$ instances for $\FiniteWindowMetaCICDiamondEnvelopeUp$ at the displayed finite carrier surface
$$
W,R,J,F,L,O,G,H,C,P,N .
$$
Those instances must certify that the packet is neither empty nor field-forgetting: every accepted carrier visibly retains the bounded peak window, residual-substitution boundary, residual-join determinacy row, parallel-diamond frontier, closed-premise ledger, obstruction-retention row, transport, replay, provenance, and local NameCert data.
\end{theorem}
\begin{proof}
The readiness row $G$ in \autoref{def:finite-window-metacic-diamond-envelope-carrier} is tied to the whole envelope, not to the residual-join row alone.

Nontriviality must exhibit an accepted packet with all displayed rows present. FieldFaithfulness must show that deleting any of $W,R,J,F,L,O,H,C,P,N$ changes the readable carrier surface. Thus the TasteGate burden remains exactly at the finite residual-window diamond-envelope boundary.
\end{proof}

\closureat{FiniteWindowMetaCICDiamondEnvelopeUp}{seedStr}

\begin{closurestatus}{\FiniteWindowMetaCICDiamondEnvelopeUp}
  \constructivestory{A $\FiniteWindowMetaCICDiamondEnvelopeUp$ packet is generated from a bounded MetaCIC peak-window row, residual-substitution boundary row, residual-join determinacy row, parallel-diamond frontier row, closed parallel-diamond premise ledger row, obstruction-retention row, Nontrivial and FieldFaithful TasteGate readiness, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-window-metacic-diamond-envelope-carrier}, \autoref{thm:finite-window-metacic-diamond-envelope-namecert-obligations}, \autoref{thm:finite-window-metacic-diamond-envelope-handoff}, and \autoref{thm:finite-window-metacic-diamond-envelope-tastegate-scope} seed the finite residual-window diamond envelope for MetaCIC confluence-audit consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close residual-substitution compatibility, a premise-free parallel diamond, arbitrary closed Church--Rosser, subject reduction, evaluator equality, quotient conversion equality, selected joins, kernel consistency, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, peak-window exposure, residual-substitution boundary retention, residual-join determinacy, parallel-diamond frontier handoff, closed-premise ledger exposure, obstruction retention, TasteGate nontriviality, FieldFaithful coverage, transport, replay, provenance, and local naming for BEDC.Derived.FiniteWindowMetaCICDiamondEnvelopeUp.}
\end{closurestatus}
