\chapter{A Concrete Naming Certificate for $\LawlikeCauchyRealUp$}
\label{ch:concrete-instances-lawlike-cauchy-real-namecert}
\origin{human}

Following Bishop and Bridges, the $\LawlikeCauchyRealUp$ packet presents a real number by a lawlike regular Cauchy rational name whose request schedule is visible before any quotient, selected limit, countable-choice principle, or ambient completeness theorem is read. It sits on the lawlike generation discipline of \autoref{ch:concrete-instances-lawlike-sequence-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the Cauchy-modulus interface of \autoref{ch:concrete-instances-cauchymodulus-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet records a non-quotient, choice-free Real-and-Completion route; it does not assert that arbitrary Cauchy data carries a selected Real limit.

\begin{definition}[LawlikeCauchyReal carrier]
\label{def:lawlike-cauchy-real-carrier}
A $\LawlikeCauchyRealUp$ carrier is a finite $\BHist$ packet
$$
L=(G,S,D,Q,M,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the $\LawlikeSequenceUp$ generation row, recording the lawlike request procedure that produces the rational observations.
\item $S$ is the $\StreamNameUp$ finite-window row opened by the displayed request procedure.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording dyadic error budgets, endpoint comparisons, and late-window bounds.
\item $Q$ is the $\RegSeqRatUp$ readback row produced from the lawlike stream windows and dyadic tolerance ledger.
\item $M$ is the $\CauchyModulusSpaceUp$ row naming the displayed modulus schedule or convergence budget consumed by the regular readback.
\item $E$ is the terminal $\RealUp$ seal row reached only after $G,S,D,Q,M$ have all been exposed.
\item $H$ records componentwise $\hsame$ transport for the lawlike generator, stream window, dyadic ledger, regular readback, modulus row, Real seal, replay row, provenance row, and local naming row.
\item $C$ records displayed $\Cont$ replay from a lawlike Cauchy real request through $G,S,D,Q,M,E$.
\item $P$ is the $\Pkg$ provenance over $\LawlikeCauchyRealUp$, $\LawlikeSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyModulusSpaceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LawlikeCauchyRealUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $G,S,D,Q,M,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected limits, countable-choice schedules, host real equality, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge credentials.
\end{definition}

\begin{theorem}[LawlikeCauchyReal NameCert obligations]
\label{thm:lawlike-cauchy-real-namecert-obligations}
For every accepted $\LawlikeCauchyRealUp$ carrier
$$
L=(G,S,D,Q,M,E,H,C,P,N),
$$
the local $\NameCert_{\LawlikeCauchyRealUp}$ surface consists exactly of carrier admission, lawlike generator exposure, finite stream-window exposure, dyadic tolerance exactness, regular rational readback, displayed Cauchy-modulus handoff, Real-seal routing, componentwise transport, displayed replay, provenance, local naming, and non-escape from the displayed rows.
\end{theorem}
\begin{proof}
Project the carrier rows of \autoref{def:lawlike-cauchy-real-carrier}. The accepted packet exposes the lawlike generator $G$, the stream window $S$, the dyadic ledger $D$, the regular readback $Q$, the modulus row $M$, the Real seal $E$, and the structural rows $H,C,P,N$.

The source rows are then read in order. The lawlike procedure of \autoref{ch:concrete-instances-lawlike-sequence-namecert} supplies the request discipline, \autoref{ch:concrete-instances-streamname-namecert} opens only the finite windows requested by that procedure, and \autoref{ch:concrete-instances-dyadicratcore-namecert} supplies the tolerance ledger.

The regular and completion-facing rows close the route without adding a selected limit. The readback of \autoref{ch:concrete-instances-regseqrat-namecert} packages the finite rational data, \autoref{ch:concrete-instances-cauchymodulus-namecert} supplies the displayed budget row, and \autoref{ch:concrete-instances-real-namecert} receives the terminal seal only through $E$.

Finally $H$ and $C$ transport and replay the same coordinates, while $P$ and $N$ record provenance and local naming. Since no additional coordinate is present, the certificate surface exports none of the excluded quotient, choice, completeness, host-equality, verification, or bridge data.
\end{proof}

\begin{theorem}[LawlikeCauchyReal modulus handoff]
\label{thm:lawlike-cauchy-real-modulus-handoff}
Every completion-facing request for an accepted $\LawlikeCauchyRealUp$ carrier reads the displayed Cauchy modulus row $M$ only after the lawlike generator $G$, finite stream window $S$, dyadic tolerance ledger $D$, and regular rational readback $Q$ have been exposed. Thus the handoff supplies a finite convergence budget for the named lawlike route, not a selector for arbitrary Cauchy data.
\end{theorem}
\begin{proof}
Start with an accepted carrier $L=(G,S,D,Q,M,E,H,C,P,N)$. By \autoref{def:lawlike-cauchy-real-carrier}, the only Cauchy-modulus coordinate is $M$, and it is downstream of the lawlike source, finite window, tolerance ledger, and regular readback rows.

The sibling routes determine the inputs to $M$. The generator row $G$ supplies a lawlike request discipline, the window row $S$ opens the requested observations, the dyadic row $D$ supplies the tolerance comparisons, and the regular row $Q$ packages those observations as the readback expected by the modulus interface.

Therefore a completion-facing consumer cannot read $M$ as ambient completeness or as a selected limit. The only accepted handoff is the displayed route through $G,S,D,Q,M$, transported by $H$, replayed by $C$, and named by $P,N$.
\end{proof}

\begin{theorem}[LawlikeCauchyReal Real seal]
\label{thm:lawlike-cauchy-real-real-seal}
Every $\RealUp$-facing read exported by an accepted $\LawlikeCauchyRealUp$ carrier factors through the finite route
$$
G,S,D,Q,M \longmapsto E
$$
before the terminal Real seal is visible. Thus a consumer receives lawlike generation, finite StreamName windows, dyadic tolerance rows, RegSeqRat readback, and the CauchyModulusSpace budget before it may consume the $\RealUp$ row.
\end{theorem}
\begin{proof}
Apply \autoref{thm:lawlike-cauchy-real-namecert-obligations}. The Real-facing coordinate is $E$, and the obligation surface places it after $G,S,D,Q,M$.

The route cannot bypass the source stage because $G$ is the only row naming the lawlike request procedure. It cannot bypass the window or tolerance stage because $S$ and $D$ are the only rows containing finite observations and dyadic error bounds.

The regular readback and modulus handoff are also forced. The row $Q$ is the sole $\RegSeqRatUp$ readback available to the packet, and $M$ is the sole displayed $\CauchyModulusSpaceUp$ budget consumed before the Real seal.

Transport, replay, provenance, and local naming preserve the same route. Since $H,C,P,N$ add no quotient, selected-limit, countable-choice, host-equality, or ambient-completeness coordinate, every Real-facing read reaches $E$ only through the displayed route.
\end{proof}

\begin{theorem}[LawlikeCauchyReal non-escape]
\label{thm:lawlike-cauchy-real-nonescape}
An accepted $\LawlikeCauchyRealUp$ carrier exports no quotient stream equality, selected limit, countable-choice schedule, trichotomy principle, open-cover compactness proof, ambient $\RealUp$ completeness theorem, host real equality, Lean verification, or bridge credential. Every exported read is confined to $G,S,D,Q,M,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Use the carrier definition to enumerate the available coordinates. They are exactly the lawlike generator, stream window, dyadic ledger, regular readback, modulus row, Real seal, transport, replay, provenance, and local naming rows.

The obligation theorem identifies the NameCert surface with those same rows. Any proposed exported read must therefore be one of the displayed coordinates or a structural transport of them through $H$ and $C$.

None of the displayed coordinates stores quotient stream equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient Real completeness, host real equality, Lean verification, or bridge data. Hence no such datum can escape from the packet.
\end{proof}

\closureat{LawlikeCauchyRealUp}{seedStr}

\begin{closurestatus}{\LawlikeCauchyRealUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lawlike-cauchy-real-carrier}, \autoref{thm:lawlike-cauchy-real-namecert-obligations}, \autoref{thm:lawlike-cauchy-real-modulus-handoff}, \autoref{thm:lawlike-cauchy-real-real-seal}, and \autoref{thm:lawlike-cauchy-real-nonescape} seed the non-quotient lawlike Cauchy real-name packet over displayed $\LawlikeSequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyModulusSpaceUp$, and $\RealUp$ rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient real equality, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, lawlike generator exposure, stream-window exposure, dyadic tolerance exactness, regular rational readback, displayed Cauchy-modulus handoff, Real-seal routing, transport stability, replay stability, provenance, local naming, and non-escape for BEDC.Derived.LawlikeCauchyRealUp.}
  \constructivestory{A $\LawlikeCauchyRealUp$ packet is generated from a $\LawlikeSequenceUp$ request procedure, finite $\StreamNameUp$ windows, a $\DyadicRatCoreUp$ tolerance ledger, a $\RegSeqRatUp$ readback row, a $\CauchyModulusSpaceUp$ budget row, a terminal $\RealUp$ seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
\end{closurestatus}
