\chapter{A Concrete Naming Certificate for $\RiemannSumCauchyNetUp$}
\label{ch:concrete-instances-riemann-sum-cauchy-net-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RiemannSumCauchyNetUp$ packet records the finite Cauchy-net bridge by which dyadic Riemann sums become completion-facing data without importing ambient real completeness. It sits after the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, the Cauchy boundary of \autoref{ch:concrete-instances-cauchy-namecert}, and the finite mesh discipline of \autoref{ch:concrete-instances-riemann-uniform-mesh-namecert}. The packet names the finite net of dyadic Riemann-sum approximants; it is not a host integrability theorem, a selected limit, a quotient completion, or an ambient $\RealUp$ completeness principle.

\begin{definition}[Riemann sum Cauchy-net carrier]
\label{def:riemann-sum-cauchy-net-carrier}
A $\RiemannSumCauchyNetUp$ carrier is a finite $\BHist$ packet
$$
K=(D,W,R,M,S,E,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the dyadic mesh depth, endpoint budget, and comparison scale used by the net;
\item $W$ is the $\StreamNameUp$ finite-window row opened at that dyadic scale;
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same windows and dyadic tolerances;
\item $M$ is the finite $\RiemannUniformMeshUp$ mesh row through which partition widths and tagged cells are inspected;
\item $S$ is the dyadic Riemann-sum row, recording the finite sum visible after $D,W,R,M$ are displayed;
\item $E$ is the terminal $\RealUp$ seal for the current finite approximation;
\item $Q$ is the $\CauchyUp$ comparison row, recording that two displayed mesh depths have a dyadic tolerance comparison inside the same finite packet;
\item $H$ records componentwise $\hsame$ transport for the dyadic, window, readback, mesh, sum, Real, Cauchy, replay, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ replay of the route
$$
D,W,R,M \longmapsto S \longmapsto E \longmapsto Q ;
$$
\item $P$ is the $\Pkg$ provenance over $\RiemannSumCauchyNetUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RiemannUniformMeshUp$, $\RealUp$, $\CauchyUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\RiemannSumCauchyNetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,W,R,M,S,E,Q,H,C,P,N$. It has no coordinate for a host integral, ambient real completeness, quotient equality of nets, selected limiting value, or unrestricted choice of partitions.
\end{definition}

\begin{theorem}[Riemann sum Cauchy-net NameCert obligations]
\label{thm:riemann-sum-cauchy-net-namecert-obligations}
For every accepted $\RiemannSumCauchyNetUp$ carrier $K=(D,W,R,M,S,E,Q,H,C,P,N)$, the local $\NameCert_{\RiemannSumCauchyNetUp}$ surface consists exactly of carrier admission; dyadic tolerance exposure through $D$; finite-window inspection through $W$; regular rational readback through $R$; uniform mesh exposure through $M$; finite Riemann-sum handoff through $S$; terminal Real sealing through $E$; Cauchy comparison through $Q$; componentwise transport through $H$; displayed replay through $C$; package provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:riemann-sum-cauchy-net-carrier}. The displayed rows are exactly $D,W,R,M,S,E,Q,H,C,P,N$, so each local obligation must be discharged by one of those finite coordinates.

The upstream route is dyadic and finite. The row $D$ fixes the tolerance ledger, $W$ opens only the requested finite windows, $R$ records the regular rational readback, and $M$ supplies the uniform mesh cells used by the Riemann-sum row.

The downstream route is sum, seal, and comparison. The row $S$ exports only the finite dyadic Riemann sum, $E$ seals the current approximation as $\RealUp$ data, and $Q$ records the Cauchy comparison between displayed mesh depths.

Finally transport, replay, provenance, and local naming preserve the same packet through $H,C,P,N$. Since host integrals, quotient nets, selected limits, unrestricted partitions, and ambient real completeness are absent from the carrier, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Riemann sum Cauchy-net Real-completion handoff]
\label{thm:riemann-sum-cauchy-net-real-completion-handoff}
Every completion-facing consumer of an accepted $\RiemannSumCauchyNetUp$ packet receives a finite handoff
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RiemannUniformMeshUp,\ \RealUp,\ \CauchyUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
The consumer may read the $\RealUp$ seal only after the dyadic tolerance, finite-window, regular readback, uniform-mesh, and finite-sum rows have been displayed, and may read the $\CauchyUp$ comparison only as a finite tolerance comparison between two displayed mesh depths. The handoff supplies no ambient completion of Riemann sums, selected integral value, quotient equality of Cauchy nets, or host real-completeness coordinate.
\end{theorem}
\begin{proof}
Start with an accepted carrier $K=(D,W,R,M,S,E,Q,H,C,P,N)$. The Real-facing row $E$ is downstream of the dyadic tolerance row $D$, finite window row $W$, regular readback row $R$, uniform mesh row $M$, and finite sum row $S$.

The Cauchy-facing row $Q$ is also downstream of those displayed approximants. It records a finite tolerance comparison between two visible mesh depths, not a completed quotient net or a selected endpoint.

Use $H,C,P,N$ to transport, replay, source, and name the same route. A completion-facing consumer therefore receives the finite dyadic Riemann-sum Cauchy-net packet and not an ambient real-completeness principle.
\end{proof}

\falsifiablePrediction{If a completion-facing consumer reaches the $\RealUp$ seal $E$ or the $\CauchyUp$ comparison row $Q$ without first displaying the dyadic tolerance, StreamName window, RegSeqRat readback, uniform mesh, finite-sum, transport, replay, provenance, and local NameCert rows, the $\RiemannSumCauchyNetUp$ carrier has been misread.}

\independenceWitness{dyadicratcore, streamname, regseqrat, riemann-uniform-mesh, real, and cauchy are not individually bijective with $\RiemannSumCauchyNetUp$ because this packet jointly carries dyadic tolerances, finite observation windows, regular readback, uniform mesh rows, finite Riemann sums, Real seals, Cauchy comparisons, transport, replay, provenance, and local naming.}

\closureat{RiemannSumCauchyNetUp}{seedStr}

\begin{closurestatus}{\RiemannSumCauchyNetUp}
  \constructivestory{A $\RiemannSumCauchyNetUp$ packet is generated from a DyadicRatCore tolerance ledger, StreamName finite windows, RegSeqRat readback, RiemannUniformMesh rows, a finite Riemann-sum row, a Real seal, a Cauchy comparison row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riemann-sum-cauchy-net-carrier}, \autoref{thm:riemann-sum-cauchy-net-namecert-obligations}, and \autoref{thm:riemann-sum-cauchy-net-real-completion-handoff} seed the finite dyadic Riemann-sum Cauchy-net bridge consumed by Real and completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Riemann integrability, ambient Real completeness, quotient Cauchy nets, selected integral values, unrestricted partition choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dyadic tolerance exposure, finite-window inspection, regular rational readback, uniform mesh exposure, finite-sum handoff, Real sealing, Cauchy comparison, transport, replay, provenance, and local naming for BEDC.Derived.RiemannSumCauchyNetUp.}
\end{closurestatus}
