\chapter{A Concrete Naming Certificate for $\HyperbolicPattersonSullivanShadowUp$}
\label{ch:concrete-instances-hyperbolic-patterson-sullivan-shadow-namecert}
\origin{human}

Following Patterson and Sullivan on hyperbolic limit-set shadows, the $\HyperbolicPattersonSullivanShadowUp$ packet records a finite shadow ledger for boundary-weight readout. It sits after the visual-metric certificate of \autoref{ch:concrete-instances-hyperbolic-visual-metric-namecert}, the boundary-shadow route of \autoref{ch:concrete-instances-hyperbolic-boundary-shadow-namecert}, the Busemann-boundary certificate of \autoref{ch:concrete-instances-hyperbolic-busemann-boundary-namecert}, and the geodesic-flow carrier of \autoref{ch:concrete-instances-hyperbolic-geodesic-flow-namecert}. The packet names a displayed Patterson--Sullivan shadow surface over finite boundary, window, counting, transport, replay, provenance, and local naming rows; it is not a completed conformal density, quotient limit set, ambient ergodic theorem, host hyperbolic group action, or global measure construction.

\begin{definition}[Hyperbolic Patterson-Sullivan shadow carrier]
\label{def:hyperbolic-patterson-sullivan-shadow-carrier}
A $\HyperbolicPattersonSullivanShadowUp$ carrier is a finite $\BHist$ packet
$$
S=(B,V,W,C,R,H,K,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the boundary basepoint row, naming the finite Busemann-boundary face from which the shadow is observed.
\item $V$ is the $\HyperbolicVisualMetricUp$ row, displaying the visual metric comparison used to read the boundary shadow.
\item $W$ is the shadow-window row, recording the finite boundary-shadow aperture and the accepted visible window.
\item $C$ is the critical exponent and counting-budget row, recording the finite growth bound under which the shadow ledger is admitted.
\item $R$ is the Busemann transport row, tying the basepoint, visual metric, shadow window, and counting budget to one boundary-facing route.
\item $H$ records componentwise $\hsame$ transport for $B,V,W,C,R,K,P,N$.
\item $K$ records displayed $\Cont$ replay from boundary-basepoint admission through visual-metric readback, shadow-window exposure, critical-exponent counting, and Busemann transport.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicPattersonSullivanShadowUp$, $\HyperbolicVisualMetricUp$, $\HyperbolicBoundaryShadowUp$, $\HyperbolicBusemannBoundaryUp$, $\HyperbolicGeodesicFlowUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicPattersonSullivanShadowUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $B,V,W,C,R,H,K,P,N$. It has no coordinate for a completed conformal density, quotient limit set, ambient ergodic theorem, host group action, global measure construction, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Hyperbolic Patterson-Sullivan shadow NameCert obligations]
\label{thm:hyperbolic-patterson-sullivan-shadow-namecert-obligations}
For every accepted $\HyperbolicPattersonSullivanShadowUp$ carrier $S=(B,V,W,C,R,H,K,P,N)$, the local $\NameCert_{\HyperbolicPattersonSullivanShadowUp}$ surface consists exactly of boundary-basepoint admission, visual-metric row exposure, shadow-window admission, critical-exponent and counting-budget ledger exposure, Busemann transport, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming. These five NameCert obligations are carrier admission for $B,V,W,C$, route exactness through $R$, transport stability through $H$, replay stability through $K$, and provenance-local-name exhaustion through $P,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-patterson-sullivan-shadow-carrier}. The displayed tuple exposes the boundary basepoint, visual-metric row, shadow-window row, critical exponent and counting budget, Busemann transport, and the structural rows.

The first obligation is carrier admission: $B,V,W,C$ are the only geometric and counting rows admitted by the packet. The second obligation is route exactness: $R$ ties those rows into one Busemann-transport route before any shadow ledger can be read.

The remaining obligations are structural. The row $H$ gives componentwise $\hsame$ transport, $K$ replays the same route by displayed $\Cont$, and $P,N$ record provenance and local naming. Since the carrier has no coordinate for a completed conformal density, quotient limit set, ambient ergodic theorem, host group action, global measure construction, Lean verification, or bridge checking, these rows exhaust the NameCert surface.
\end{proof}

\falsifiablePrediction{Every accepted $\HyperbolicPattersonSullivanShadowUp$ read must expose a boundary basepoint, $\HyperbolicVisualMetricUp$ row, $\HyperbolicBoundaryShadowUp$ window, critical-exponent counting budget, $\HyperbolicBusemannBoundaryUp$ transport, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming before it exports a public shadow ledger.}

\independenceWitness{hyperbolic-visual-metric, hyperbolic-boundary-shadow, hyperbolic-busemann-boundary, hyperbolic-geodesic-flow: no listed sibling is bijective to $\HyperbolicPattersonSullivanShadowUp$ because this packet jointly carries boundary-basepoint admission, visual comparison, shadow-window exposure, critical-exponent counting, Busemann transport, replay, provenance, and local NameCert rows.}

\closureat{HyperbolicPattersonSullivanShadowUp}{seedStr}

\begin{closurestatus}{\HyperbolicPattersonSullivanShadowUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-patterson-sullivan-shadow-carrier} and \autoref{thm:hyperbolic-patterson-sullivan-shadow-namecert-obligations} seed the finite Patterson--Sullivan shadow ledger through boundary basepoints, visual metrics, shadow windows, counting budgets, Busemann transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close completed conformal densities, quotient limit sets, ambient ergodic theorems, host hyperbolic group actions, global measure constructions, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, visual-metric exposure, shadow-window admission, critical-exponent counting, Busemann transport, replay stability, provenance exhaustion, and TasteGate field faithfulness for BEDC.Derived.HyperbolicPattersonSullivanShadowUp.}
  \constructivestory{A $\HyperbolicPattersonSullivanShadowUp$ packet is generated from a boundary basepoint, visual-metric row, shadow-window row, critical-exponent counting-budget row, Busemann transport, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
\end{closurestatus}
