\chapter{A Concrete Naming Certificate for $\LocalizedCauchySubsequenceUp$}
\label{ch:concrete-instances-localized-cauchy-subsequence-namecert}
\origin{human}

Following Bishop and Bridges, the $\LocalizedCauchySubsequenceUp$ packet records the finite subsequence-window extraction used by the constructive Real and completion route. It reads the bounded $\RealUp$ windows of \autoref{ch:concrete-instances-real-namecert}, the prefix schedules of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite extraction surface of \autoref{ch:concrete-instances-bolzano-cauchy-namecert}, and the criterion route of \autoref{ch:concrete-instances-cauchy-convergence-criterion-namecert}. The packet names a local finite window, not an ambient completeness theorem, a selected host limit, or a countable-choice subsequence selector.

\begin{definition}[Localized Cauchy subsequence carrier]
\label{def:localized-cauchy-subsequence-carrier}
A $\LocalizedCauchySubsequenceUp$ carrier is a finite $\BHist$ packet
$$
Q=(W,S,R,D,B,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the bounded $\RealUp$ window row. It records the finite source interval, endpoint seals, and bounded comparison rows in which the subsequence extraction is inspected.
\item $S$ is the $\StreamNameUp$ prefix schedule. It displays the finite source prefixes, candidate subsequence indices, and monotone prefix inclusions used by the local extraction.
\item $R$ is the $\RegSeqRatUp$ readback row for the selected prefix windows and their rational regularity data.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the dyadic scales, rational comparisons, and exhaustion budget used to test local Cauchy behavior.
\item $B$ is the $\BolzanoCauchyUp$ route row. It exposes the finite subsequence-window extraction surface without exporting a selected host limit.
\item $E$ is the $\CauchyConvergenceCriterionUp$ endpoint row that can be read only after $W,S,R,D,B$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the bounded Real window, stream prefixes, regular rational readbacks, dyadic ledger, Bolzano-Cauchy route, criterion endpoint, continuation, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a local tolerance request through $W,S,R,D,B,E$ and then through the structural rows.
\item $P$ is the $\Pkg$ provenance over $\LocalizedCauchySubsequenceUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\BolzanoCauchyUp$, $\CauchyConvergenceCriterionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocalizedCauchySubsequenceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. It has no coordinate for ambient $\RealUp$ completeness, quotient stream equality, a host-selected limit, an infinite selector, open-cover compactness, or countable choice.
\end{definition}

\begin{theorem}[Localized Cauchy subsequence NameCert obligations]
\label{thm:localized-cauchy-subsequence-namecert-obligations}
For every accepted $\LocalizedCauchySubsequenceUp$ carrier
$$
Q=(W,S,R,D,B,E,H,C,P,N),
$$
the local $\NameCert_{\LocalizedCauchySubsequenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the bounded Real window, StreamName prefixes, RegSeqRat readback, DyadicRatCore tolerance ledger, Bolzano-Cauchy route, Cauchy-convergence endpoint, transport, replay, provenance, and local naming rows;
\item local-window exposure, requiring every subsequence read to display $W$ before it can inspect $S,R,D$;
\item finite extraction routing, requiring every subsequence candidate to pass through $S,R,D$ and the $\BolzanoCauchyUp$ row $B$ before the criterion endpoint $E$ is available;
\item structural stability, requiring $H$ and $C$ to preserve and replay only the displayed finite route;
\item ledger non-escape, requiring $P$ and $N$ to name no object outside the displayed packet.
\end{enumerate}
No localized subsequence obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:localized-cauchy-subsequence-carrier}. The visible coordinates are exactly the bounded Real window, prefix schedule, rational readback, dyadic ledger, Bolzano-Cauchy route, criterion endpoint, and the structural support rows.

The local-window obligation is forced by the row order. A subsequence read first sees the bounded $\RealUp$ window $W$, and only then can it inspect the finite prefixes $S$, readbacks $R$, and tolerances $D$.

The extraction route is the finite route through $\BolzanoCauchyUp$ and $\CauchyConvergenceCriterionUp$. The rows $B$ and $E$ are downstream of $S,R,D$, so no endpoint can be exported before the local subsequence window has been displayed.

Finally, $H,C,P,N$ transport, replay, source, and name that same packet. Since the carrier has no further coordinate, the five listed obligation rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Localized Cauchy subsequence window extraction]
\label{thm:localized-cauchy-subsequence-window-extraction}
Every accepted $\LocalizedCauchySubsequenceUp$ carrier exposes a finite subsequence-window route
$$
W \longmapsto S \longmapsto R \longmapsto D \longmapsto B \longmapsto E \longmapsto H,C,P,N
$$
before any Cauchy criterion endpoint can be consumed. The route may be read by Real and completion consumers only through the displayed $\RealUp$ window, $\StreamNameUp$ prefixes, $\RegSeqRatUp$ readbacks, $\DyadicRatCoreUp$ tolerance ledger, $\BolzanoCauchyUp$ extraction row, and $\CauchyConvergenceCriterionUp$ endpoint. It exports no ambient completeness principle, selected host limit, countable-choice subsequence selector, quotient stream equality, or open-cover compactness row.
\end{theorem}
\begin{proof}
Start with an accepted carrier. By \autoref{def:localized-cauchy-subsequence-carrier}, the only source of bounded sequence data is $W$, the only prefix data are $S$, and the only rational and dyadic tolerance data are $R$ and $D$.

Apply \autoref{thm:localized-cauchy-subsequence-namecert-obligations}. It requires any subsequence candidate to display $W,S,R,D$ and then pass through the $\BolzanoCauchyUp$ route row $B$ before the Cauchy-convergence endpoint $E$ is public.

The structural rows do not add a second route. They preserve, replay, source, and name the same finite packet, so a Real or completion consumer can only receive the displayed route.

The excluded principles are absent from the carrier inventory. Hence the extraction remains a local finite subsequence-window route rather than an ambient completeness or choice construction.
\end{proof}

\falsifiablePrediction{Every $\LocalizedCauchySubsequenceUp$ read must display a bounded Real window, StreamName prefixes, RegSeqRat readback, DyadicRatCore tolerances, BolzanoCauchy routing, a CauchyConvergenceCriterion endpoint, transport, replay, provenance, and local naming before any Cauchy endpoint is consumed.}

\independenceWitness{real, streamname, regseqrat, dyadicratcore, bolzano-cauchy, cauchy-convergence-criterion: $\LocalizedCauchySubsequenceUp$ is not bijective to any listed sibling because it jointly carries the bounded local window, finite prefix extraction, tolerance ledger, criterion endpoint, transport, replay, provenance, and local naming.}

\closureat{LocalizedCauchySubsequenceUp}{seedStr}

\begin{closurestatus}{\LocalizedCauchySubsequenceUp}
  \constructivestory{A $\LocalizedCauchySubsequenceUp$ packet is generated from a bounded RealUp window, StreamName prefix schedule, RegSeqRat readback, DyadicRatCore tolerance ledger, BolzanoCauchy route, CauchyConvergenceCriterion endpoint, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:localized-cauchy-subsequence-carrier}, \autoref{thm:localized-cauchy-subsequence-namecert-obligations}, and \autoref{thm:localized-cauchy-subsequence-window-extraction} seed the finite localized subsequence-window route for Real and completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient RealUp completeness, quotient stream equality, selected host limits, countable-choice subsequence selection, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, local-window exposure, finite extraction routing, structural stability, and ledger non-escape for BEDC.Derived.LocalizedCauchySubsequenceUp.}
\end{closurestatus}
