\chapter{A Concrete Naming Certificate for $\RealCompletenessGapRouterUp$}
\label{ch:concrete-instances-real-completeness-gap-router-namecert}
\origin{ai}

The $\RealCompletenessGapRouterUp$ packet realizes the boundary route of \autoref{ch:visions-real-completeness} as finite BEDC data separating permitted StreamName, RegSeqRat, DyadicRatCore, and RealUp reads from off-table completeness claims. It sits after the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the exact completion boundary of \autoref{ch:concrete-instances-real-completion-exact-boundary-namecert}. The packet is a gate for what may be read at the completion boundary, not an assertion of ambient $\RealUp$ completeness.

\begin{definition}[Real completeness gap-router carrier]
\label{def:real-completeness-gap-router-carrier}
A $\RealCompletenessGapRouterUp$ carrier is a finite $\BHist$ packet
$$
G=(S,Q,D,R,A,O,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ window row through which every completion-boundary request exposes finite observations.
\item $Q$ is the $\RegSeqRatUp$ readback row assembled from the displayed windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger governing the requested precision.
\item $R$ is the $\RealUp$ seal row available only after $S,Q,D$ have been displayed.
\item $A$ is the allowed-read ledger listing the finite routes a completion consumer may inspect.
\item $O$ is the off-table ledger naming refused reads: quotient streams, selected limits, host real equality, choice schedules, and ambient completeness.
\item $T$ is the TasteGate obligation row requiring allowed reads to remain finite, routed, and separately auditable from refused completeness claims.
\item $H$ records componentwise $\hsame$ transport for the window, readback, tolerance, Real seal, allowed-read, off-table, TasteGate, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-boundary request through $S,Q,D,R,A,O,T,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RealCompletenessGapRouterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\RealCompletionExactBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RealCompletenessGapRouterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,Q,D,R,A,O,T,H,C,P,N$. It has no coordinate for quotient real equality, selected representatives, countable choice, host limits, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Real completeness gap-router NameCert obligations]
\label{thm:real-completeness-gap-router-namecert-obligations}
For every accepted $\RealCompletenessGapRouterUp$ carrier
$$
G=(S,Q,D,R,A,O,T,H,C,P,N),
$$
the local $\NameCert_{\RealCompletenessGapRouterUp}$ surface consists exactly of finite window exposure through $S$, regular rational readback through $Q$, dyadic tolerance visibility through $D$, terminal Real sealing through $R$, allowed-read routing through $A$, refused-read separation through $O$, TasteGate obligations through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, sibling provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:real-completeness-gap-router-carrier}. Its public rows are exactly $S,Q,D,R,A,O,T,H,C,P,N$, so any completion-boundary read must be witnessed by those rows.

The allowed side is finite. StreamName windows, RegSeqRat readback, DyadicRatCore tolerances, and the Real seal are displayed separately before the allowed-read ledger is consumed.

The refused side is explicit. The off-table ledger $O$ records quotient streams, selected limits, host equality, choice schedules, and ambient completeness as absent rows, while $T$ states the TasteGate obligation that allowed reads remain finite and routed.

Transport and replay preserve the same split through $H$ and $C$, and $P,N$ source and name it. No additional completion object exists in the carrier, so the listed obligations exhaust the gap-router surface.
\end{proof}

\begin{theorem}[Real completeness gap-router allowed-read route]
\label{thm:real-completeness-gap-router-allowed-read-route}
Every allowed completion-boundary read consumed from an accepted $\RealCompletenessGapRouterUp$ packet factors through
$$
\StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp
$$
and then through the allowed-read ledger $A$ and TasteGate row $T$. The same read must keep the off-table ledger $O$ visible, so it cannot be promoted to quotient stream equality, selected-limit construction, host real equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:real-completeness-gap-router-namecert-obligations}. They require each accepted read to expose $S,Q,D,R$ before the allowed-read ledger $A$ is consumed.

The TasteGate row $T$ then checks that the route is finite, separately auditable, and sourced by the displayed StreamName, RegSeqRat, DyadicRatCore, and RealUp rows. The row does not contain a completion theorem or a bridge credential.

Finally the off-table ledger $O$ stays visible along the same route. Since the refused objects have no carrier coordinate, the allowed read cannot become quotient equality, selected limits, host equality, choice, or ambient completeness.
\end{proof}

\begin{theorem}[Real completeness gap-router exact-boundary separation]
\label{thm:real-completeness-gap-router-exact-boundary-separation}
The $\RealCompletenessGapRouterUp$ route may consume $\RealCompletionExactBoundaryUp$ only as a finite sibling boundary over StreamName, RegSeqRat, DyadicRatCore, and RealUp rows. It does not convert that sibling boundary into a completed Real object, a selected representative, a quotient stream, or a host completeness theorem.
\end{theorem}
\begin{proof}
Read the provenance row $P$ in \autoref{def:real-completeness-gap-router-carrier}. It cites $\RealCompletionExactBoundaryUp$ beside the four displayed source faces, so the exact-boundary sibling is a routed dependency rather than a new coordinate of completed real equality.

Apply the allowed-read route theorem, \autoref{thm:real-completeness-gap-router-allowed-read-route}. Any consumer must still pass through StreamName, RegSeqRat, DyadicRatCore, RealUp, the allowed ledger, the TasteGate row, and the off-table ledger.

Thus the sibling exact-boundary read remains finite and separated from the refused completion objects. The gap router exposes the boundary and the refusal ledger together, and no host completeness theorem is available for export.
\end{proof}

\falsifiablePrediction{Every accepted $\RealCompletenessGapRouterUp$ completion-boundary read must display StreamName, RegSeqRat, DyadicRatCore, RealUp, allowed-read, off-table, TasteGate, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows before any Real-facing output is visible.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, real-completion-exact-boundary: $\RealCompletenessGapRouterUp$ is not bijective to any listed sibling because it jointly carries allowed-read rows, off-table refusal rows, and TasteGate obligations in addition to the four finite completion-source faces.}

\closureat{RealCompletenessGapRouterUp}{seedStr}

\begin{closurestatus}{\RealCompletenessGapRouterUp}
  \constructivestory{A $\RealCompletenessGapRouterUp$ packet is generated from StreamName windows, RegSeqRat readback, DyadicRatCore tolerances, a RealUp seal, allowed-read rows, off-table refusal rows, TasteGate obligations, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-completeness-gap-router-carrier}, \autoref{thm:real-completeness-gap-router-namecert-obligations}, \autoref{thm:real-completeness-gap-router-allowed-read-route}, and \autoref{thm:real-completeness-gap-router-exact-boundary-separation} seed the finite completion-boundary router separating allowed reads from refused completeness claims.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient real equality, selected representatives, countable choice, host limit operators, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, allowed-read routing, off-table separation, TasteGate stability, transport, replay, provenance, and local naming for BEDC.Derived.RealCompletenessGapRouterUp.}
\end{closurestatus}
