\chapter{A Concrete Naming Certificate for $\CompactModulusRealizerUp$}
\label{ch:concrete-instances-compact-modulus-realizer-namecert}
\origin{human}

Following Heine--Cantor and Bishop constructive analysis, the $\CompactModulusRealizerUp$ packet realizes compact uniform continuity as a finite NameCert carrier. It reads compact finite-net data from \autoref{ch:concrete-instances-compact-namecert}, pointwise modulus rows from \autoref{ch:concrete-instances-continuousmap-namecert}, metric distance witnesses from \autoref{ch:concrete-instances-metric-namecert}, rational lower-bound folds from \autoref{ch:concrete-instances-rat-namecert}, and the finite $\mathsf{ProbeBundle}$ recursion route underlying \autoref{ch:visions-compact-uniform-continuity}. The packet is a finite uniform-modulus extraction surface, not a host open-cover compactness proof, semantic continuity theorem, or choice-selected modulus.

\begin{definition}[Compact modulus realizer carrier]
\label{def:compact-modulus-realizer-carrier}
A $\CompactModulusRealizerUp$ carrier is a finite $\BHist$ packet
$$
M=(K,F,G,Q,B,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactUp$ finite-net witness row, carrying bundled centers, located coverage rows, and finite radius data for the compact source.
\item $F$ is the $\ContinuousMapUp$ pointwise-modulus row for the displayed graph over the same source metric.
\item $G$ is the $\MetricSpaceUp$ distance-witness row, exposing source and target metric comparisons used by the triangle estimate.
\item $Q$ is the $\RatUp$ lower-bound fold row that records positive radius histories and the finite minimum ledger used to select a uniform precision.
\item $B$ is the $\mathsf{ProbeBundle}$ recursion row over the compact finite net, including bundled center names, radius rows, and fold order.
\item $U$ is the $\UniformModulusUp$ ledger row exported only after $K,F,G,Q,B$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the compact, continuous-map, metric, rational-fold, ProbeBundle, uniform-modulus, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a tolerance request through the compact finite net, pointwise moduli, metric-distance witnesses, rational lower-bound fold, ProbeBundle recursion, and uniform-modulus ledger.
\item $P$ is the $\Pkg$ provenance over $\CompactModulusRealizerUp$, $\CompactUp$, $\ContinuousMapUp$, $\MetricSpaceUp$, $\RatUp$, $\mathsf{ProbeBundle}$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactModulusRealizerUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for host open-cover compactness, semantic continuity, a choice-selected center outside the bundle, ambient completeness, quotient metric equality, or an external modulus selector.
\end{definition}

\begin{theorem}[Compact modulus realizer NameCert obligations]
\label{thm:compact-modulus-realizer-namecert-obligations}
For every accepted $\CompactModulusRealizerUp$ carrier
$$
M=(K,F,G,Q,B,U,H,C,P,N),
$$
the local $\NameCert_{\CompactModulusRealizerUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the compact finite-net witness, continuous-map pointwise modulus, metric distance witnesses, rational lower-bound fold, ProbeBundle recursion, uniform-modulus ledger, transport, replay, provenance, and local naming rows;
\item compact-source exposure, requiring every uniform-modulus request to display $K$ and $B$ before any finite lower-bound fold is read;
\item pointwise-modulus exposure, requiring the continuous-map row $F$ and metric row $G$ to supply the local distance estimates consumed by the fold;
\item rational-fold exactness, requiring $Q$ to record the selected positive lower bound through finite $\mathsf{ProbeBundle}$ recursion;
\item uniform-modulus handoff, requiring $U$ to be downstream of $K,F,G,Q,B$ and to export only the displayed tolerance-to-precision ledger;
\item structural stability, requiring $H,C,P,N$ to preserve, replay, source, and name the same finite packet.
\end{enumerate}
No compact-modulus obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-modulus-realizer-carrier}. The listed coordinates are exactly the compact finite-net witness, pointwise-modulus row, metric row, rational fold, ProbeBundle recursion row, uniform-modulus ledger, and structural rows.

The compact-source and pointwise-modulus obligations are forced by the data flow. The finite net and bundle recursion supply the centers and radius rows, while the continuous-map and metric rows supply the local estimates that can be folded.

The rational-fold exactness obligation is the role of $Q$. It records the selected positive lower bound through finite recursion over $B$, so the exported precision is a displayed history rather than an external selector.

The handoff to $U$ is therefore downstream of all analytic rows. The structural rows $H,C,P,N$ add only transport, replay, provenance, and naming, so the six listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Compact modulus ProbeBundle fold]
\label{thm:compact-modulus-realizer-probebundle-fold}
Every $\UniformModulusUp$ consumer of an accepted $\CompactModulusRealizerUp$ carrier receives its precision row only through the finite route
$$
K \longmapsto B \longmapsto F \longmapsto G \longmapsto Q \longmapsto U \longmapsto H,C,P,N .
$$
The fold is the compact finite-net and pointwise-modulus construction of \autoref{thm:compact-uniform-finite-minimum-certificate} read as concrete NameCert data: bundled compact centers supply local pointwise moduli, the $\MetricSpaceUp$ rows supply source and target distance witnesses, the $\RatUp$ fold selects a positive lower bound, and the $\UniformModulusUp$ ledger receives only that finite tolerance-to-precision route.
\end{theorem}
\begin{proof}
Start with a uniform-modulus read of the accepted carrier. By carrier admission, the only public uniform-modulus row is $U$, and it is placed after the compact finite-net row $K$, bundle recursion row $B$, pointwise-modulus row $F$, metric row $G$, and rational lower-bound row $Q$.

Read the finite compact net first. The rows $K$ and $B$ expose the bundled centers and radius histories used by primitive recursion over the finite ProbeBundle.

Next read the local analytic data. The row $F$ supplies pointwise moduli at bundled centers, while $G$ supplies the metric-distance witnesses used by the source and target triangle estimates.

Finally, the row $Q$ folds the positive radius histories into a displayed lower-bound ledger. The uniform-modulus row $U$ receives exactly that ledger with the structural rows $H,C,P,N$, and the carrier has no coordinate for host compactness, semantic continuity, external choice, ambient completeness, or quotient metric equality.
\end{proof}

\falsifiablePrediction{Every $\CompactModulusRealizerUp$ read must display CompactUp finite-net data, ContinuousMapUp pointwise-modulus rows, MetricSpaceUp distance witnesses, RatUp lower-bound folds, ProbeBundle recursion, UniformModulusUp handoff, transport, replay, provenance, and local naming.}

\independenceWitness{compact, continuousmap, metricspace, rat, probebundle, uniformmodulus: $\CompactModulusRealizerUp$ is not bijective to any listed sibling because it jointly carries compact finite nets, pointwise moduli, metric witnesses, rational lower-bound folds, ProbeBundle recursion, uniform-modulus handoff, transport, replay, provenance, and local naming.}

\closureat{CompactModulusRealizerUp}{seedStr}

\begin{closurestatus}{\CompactModulusRealizerUp}
  \constructivestory{A $\CompactModulusRealizerUp$ packet is generated from CompactUp finite-net witnesses, ContinuousMapUp pointwise-modulus rows, MetricSpaceUp distance witnesses, RatUp lower-bound folds, ProbeBundle recursion, a UniformModulusUp ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-modulus-realizer-carrier}, \autoref{thm:compact-modulus-realizer-namecert-obligations}, and \autoref{thm:compact-modulus-realizer-probebundle-fold} seed the finite compact-uniform-modulus realization surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host open-cover compactness, semantic continuity, external modulus selection, ambient completeness, quotient metric equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-source exposure, pointwise-modulus exposure, rational-fold exactness, uniform-modulus handoff, and structural stability for BEDC.Derived.CompactModulusRealizerUp.}
\end{closurestatus}
