\chapter{A Concrete Naming Certificate for $\UniformCauchyModulusExtractorUp$}
\label{ch:concrete-instances-uniform-cauchy-modulus-extractor-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy convergence, the $\UniformCauchyModulusExtractorUp$ packet records the finite readback by which one displayed uniform Cauchy witness yields an explicit modulus row before any regular rational handoff or terminal Real seal is consumed. It sits over the Real uniform surface of \autoref{ch:concrete-instances-real-uniform-structure-namecert}, the explicit-modulus sequence route of \autoref{ch:concrete-instances-effective-cauchy-sequence-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet makes finite uniform modulus extraction visible as NameCert data rather than leaving it distributed across later sequence, completion, or Real-facing chapters.

\begin{definition}[Uniform Cauchy modulus extractor carrier]
\label{def:uniform-cauchy-modulus-extractor-carrier}
A $\UniformCauchyModulusExtractorUp$ carrier is a finite $\BHist$ packet
$$
X=(U,S,M,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the uniform-Cauchy source row, naming the displayed family, tail comparison, and uniformity request from which an extraction is attempted.
\item $S$ is the $\StreamNameUp$ schedule row, recording the finite observation windows inspected from the same source.
\item $M$ is the extracted $\CauchyModulusUp$ row, storing the stage bound selected for each dyadic tolerance request.
\item $W$ is the window-realization row, recording that the selected stage from $M$ governs all retained stream windows in $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to translate requested radii, slack rows, comparison budgets, and dyadic refinements.
\item $R$ is the $\RegSeqRatUp$ readback row opened only after $U,S,M,W,D$ have been displayed.
\item $E$ is the terminal $\RealUp$ seal row available downstream of the extracted modulus and regular readback.
\item $H$ records componentwise $\hsame$ transport for the source, schedule, extracted modulus, window realization, dyadic ledger, readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a uniformity request through $U,S,M,W,D,R,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\UniformCauchyModulusExtractorUp$, $\RealUniformStructureUp$, $\EffectiveCauchySequenceUp$, $\StreamNameUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformCauchyModulusExtractorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $U,S,M,W,D,R,E,H,C,P,N$. It has no coordinate for a selected host limit, quotient stream equality, ambient $\RealUp$ completeness, countable choice, a hidden modulus oracle, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Uniform Cauchy modulus extractor NameCert obligations]
\label{thm:uniform-cauchy-modulus-extractor-namecert-obligations}
For every accepted $\UniformCauchyModulusExtractorUp$ carrier
$$
X=(U,S,M,W,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\UniformCauchyModulusExtractorUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the uniform-Cauchy source, stream schedule, extracted modulus, window realization, dyadic tolerance ledger, regular rational readback, Real seal, transport, replay, provenance, and local naming rows;
\item uniform-source exposure, requiring the extraction request to display the source row $U$ and the finite stream schedule $S$ before any modulus row is exported;
\item finite modulus extraction, requiring $M$ to be read as a displayed stage ledger and not as an external selector or hidden oracle;
\item dyadic tolerance exactness, requiring $D$ to account for requested radii, slack rows, comparison budgets, and tolerance conversions consumed by $M$ and $W$;
\item RegSeqRat and Real routing, requiring $R$ and $E$ to remain downstream of $U,S,M,W,D$;
\item transport, replay, provenance, and local naming stability for the same displayed rows through $H,C,P,N$.
\end{enumerate}
No uniform-Cauchy-modulus-extractor obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:uniform-cauchy-modulus-extractor-carrier}. The accepted packet exposes exactly the uniform-Cauchy source $U$, finite schedule $S$, extracted modulus $M$, window realization $W$, dyadic ledger $D$, regular readback $R$, Real seal $E$, and structural rows $H,C,P,N$.

The extraction row is forced to be finite. The source and schedule rows are displayed before $M$, and the dyadic ledger $D$ supplies the tolerance conversions that make the selected stages meaningful inside the packet.

The downstream route is then fixed by the EffectiveCauchySequence and Real uniform surfaces. The regular rational readback $R$ can only consume the displayed modulus, window, and tolerance rows, and the Real seal $E$ is visible only after that readback has been exposed.

Finally, $H,C,P,N$ transport, replay, source, and name the same packet. Since no host selector, quotient equality, ambient completeness theorem, hidden oracle, Lean target, or bridge certificate appears among the rows, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Uniform Cauchy modulus extractor readback route]
\label{thm:uniform-cauchy-modulus-extractor-readback-route}
Every $\RegSeqRatUp$ or $\RealUp$ consumer of an accepted $\UniformCauchyModulusExtractorUp$ carrier factors through the finite route
$$
U \longmapsto S \longmapsto M \longmapsto W \longmapsto D \longmapsto R \longmapsto E \longmapsto H,C,P,N .
$$
Thus the consumer receives a displayed uniform-Cauchy source, finite stream schedule, extracted modulus, window realization, dyadic tolerance ledger, regular readback, Real seal, transport, replay, provenance, and local naming before it can inspect any endpoint-facing result.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:uniform-cauchy-modulus-extractor-carrier}. The only regular readback row is $R$, and the only Real seal row is $E$.

The source route comes first. The uniform-Cauchy request is displayed by $U$, the finite observations are named by $S$, the extracted stage ledger is $M$, and $W$ records that the chosen stages govern the retained windows.

The dyadic accounting row $D$ then supplies the tolerance budget consumed by the readback. Hence $R$ is downstream of the source, schedule, extracted modulus, window realization, and tolerance ledger, while $E$ is downstream of $R$.

The structural rows preserve this route and add no analytic coordinate. Therefore every endpoint-facing read has exactly the stated finite factorization and cannot bypass it through excluded host or completeness data.
\end{proof}

\falsifiablePrediction{Every accepted $\UniformCauchyModulusExtractorUp$ read that reaches a RegSeqRat or Real boundary without displaying the uniform-Cauchy source, finite StreamName schedule, extracted CauchyModulus row, window realization, DyadicRatCore tolerance ledger, transport, replay, provenance, and local naming rows refutes the packet.}

\independenceWitness{real-uniform-structure, effective-cauchy-sequence, streamname, cauchymodulus, dyadicratcore, regseqrat, real: $\UniformCauchyModulusExtractorUp$ is not bijective to any listed sibling because it jointly carries a uniform-Cauchy source, finite schedule, extracted modulus, window realization, tolerance ledger, regular readback, terminal Real seal, transport, replay, provenance, and local naming.}

\closureat{UniformCauchyModulusExtractorUp}{seedStr}

\begin{closurestatus}{\UniformCauchyModulusExtractorUp}
  \constructivestory{A $\UniformCauchyModulusExtractorUp$ packet is generated from a displayed uniform-Cauchy source, finite StreamName schedule, extracted CauchyModulus row, window realization, DyadicRatCore tolerance ledger, RegSeqRat readback, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-modulus-extractor-carrier}, \autoref{thm:uniform-cauchy-modulus-extractor-namecert-obligations}, and \autoref{thm:uniform-cauchy-modulus-extractor-readback-route} seed the finite uniform modulus extraction route for Real and completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected host limits, quotient stream equality, ambient $\RealUp$ completeness, countable choice, hidden modulus oracles, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform-source exposure, finite modulus extraction, dyadic tolerance exactness, RegSeqRat and Real routing, transport, replay, provenance, and local naming for BEDC.Derived.UniformCauchyModulusExtractorUp.}
\end{closurestatus}
