\chapter{A Concrete Naming Certificate for $\ConnectionUp$}
\label{ch:concrete-instances-connection-namecert}

The connection interface $\ConnectionUp$ packages a covariant derivative on a fibre bundle, with linearity in the section argument and the Leibniz rule against scalar functions. It depends on $\NameCert_{\BundleUp}$ (\autoref{ch:concrete-instances-bundle-namecert}) and $\NameCert_{\ManifoldUp}$ (\autoref{ch:concrete-instances-manifold-namecert}), and supplies the parallel-transport and curvature substrate.

\section{Carrier definition}
\label{sec:connection-carrier}

\begin{definition}[Connection carrier packet]
\label{def:connection-carrier-packet}
A $\ConnectionUp$ carrier packet is a displayed $\mathsf{BHist}$ tuple
$$
\mathcal{C}=(\mathcal{B},\mathcal{M},b,f,s,t,\nabla,\eta_{\mathcal{B}},\eta_{\mathcal{M}},\rho)
$$
where $\mathcal{B}$ is the $\BundleUp$ source certificate, $\mathcal{M}$ is the $\ManifoldUp$ source certificate, $b:\mathsf{BHist}$ is a base-point row, $f:\mathsf{BHist}$ is the fibre row over $b$, $s:\mathsf{BHist}$ is a section row with endpoint in $f$, $t:\mathsf{BHist}$ is a tangent-direction row at $b$, and $\nabla:\mathsf{BHist}$ is the covariant-derivative endpoint row. The witnesses $\eta_{\mathcal{B}}$ and $\eta_{\mathcal{M}}$ retain the two dependency $\NameCert$ rows, while $\rho$ records that the visible source rows are compared only by the inherited $\hsame$ and classifier data supplied by $\BundleUp$ and $\ManifoldUp$.

The packet carries no ambient manifold object beyond those rows. Its public surface is the base point, fibre, section, tangent direction, derivative endpoint, dependency witnesses, and finite $\Cont$ ledger connecting the derivative endpoint back to the displayed source rows.
\end{definition}
\leandef{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket}

\begin{definition}[Connection classifier and derivative row]
\label{def:connection-classifier-and-derivative-row}
Two connection packets $\mathcal{C}$ and $\mathcal{C}'$ are classified by $\mathsf{ConnCls}$ when their base-point rows are related by the $\ManifoldUp$ point classifier, their fibre rows are related by the $\BundleUp$ fibre classifier, their section rows are related by the $\BundleUp$ section classifier, their tangent-direction rows are related by the $\ManifoldUp$ tangent classifier, and their derivative endpoint rows are related by $\hsame$. The $\mathsf{Pkg}$ provenance rows of the two dependency certificates remain part of the comparison, so a classifier witness also records the source packets from which the displayed derivative rows were read.

Thus the derivative row is a carried $\mathsf{BHist}$ endpoint, not a host-level function value. It is accepted precisely when the source base, fibre, section, and tangent rows are accepted by the inherited certificates and the endpoint comparison is witnessed by $\hsame$ inside the same finite history ledger.
\end{definition}

\begin{theorem}[Connection section-linearity obligation]
\label{thm:connection-section-linearity-obligation}
For the carrier of \autoref{def:connection-carrier-packet}, the derivative row is stable under the section-addition and scalar-action rows supplied by the $\BundleUp$ and $\ManifoldUp$ dependency sources. If $s_1$, $s_2$, and $a$ are certified section and scalar rows over the same base and tangent packet, then the derivative endpoints for $s_1+s_2$ and $a\cdot s_1$ are classified by the same $\mathsf{ConnCls}$ rows obtained by applying the corresponding carried addition and scalar-action ledgers to the derivative endpoints of $s_1$ and $s_2$.
\end{theorem}
\leanchecked{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_section\_linearity\_obligation}
\begin{proof}
Read the two section rows, their sum row, and the scalar-action row through the $\BundleUp$ certificate. The $\ManifoldUp$ source keeps the base point and tangent-direction rows fixed under the displayed classifier.

Apply endpoint transport for $\hsame$ along the finite $\Cont$ ledgers representing section addition and scalar action. The derivative endpoint row is then compared componentwise with the transported endpoint rows, while the $\mathsf{Pkg}$ provenance remains the original pair of dependency certificates.

Repack the transported base, fibre, section, tangent, and derivative comparisons into $\mathsf{ConnCls}$. No external vector-space equality is used, because all linearity data is read from the dependency rows carried by the packet.
\end{proof}

\begin{theorem}[Connection parallel-transport obligation]
\label{thm:connection-parallel-transport-obligation}
Let a displayed path spine be a finite $\mathsf{BHist}$ chain of base-point rows whose adjacent tangent-direction and derivative endpoint rows are compatible by $\mathsf{ConnCls}$. Then the chain determines a parallel-transport packet whose initial and terminal section endpoints remain in the carried fibre classifier of the $\BundleUp$ source.
\end{theorem}
\leanchecked{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_parallel\_transport\_obligation}
\begin{proof}
Induct on the displayed path spine. For the empty spine, the transport packet is the identity $\Cont$ row at the initial fibre, and the fibre classifier holds by reflexivity of the inherited $\BundleUp$ classifier.

For a nonempty spine, use the head derivative row to append one certified transport step. The compatibility premise supplies the $\hsame$ endpoint comparison needed to move from the current fibre row to the next carried fibre row.

Apply the induction hypothesis to the remaining spine and compose the two finite ledgers by $\Cont$ associativity. The terminal endpoint is therefore classified with the carried terminal fibre row by the same $\BundleUp$ classifier used at every visible step.
\end{proof}

\begin{theorem}[Connection curvature-boundary obligation]
\label{thm:connection-curvature-boundary-obligation}
Given two displayed tangent-direction rows for a connection packet, the commutator of the corresponding derivative rows is a visible $\mathsf{BHist}$ boundary row. This boundary row is consumable by $\CurvatureUp$ as the source row for the curvature packet, with base, fibre, section, tangent-pair, derivative-endpoint, and $\mathsf{Pkg}$ provenance data inherited from \autoref{def:connection-carrier-packet}.
\end{theorem}
\begin{proof}
Build the two derivative composites by appending the first tangent direction and then the second, and by appending them in the reverse order. Each composite is a finite $\Cont$ ledger over the same base, fibre, and section rows.

The commutator boundary is the displayed comparison between these two endpoint ledgers. Its source rows are exactly the two tangent-direction rows and the two derivative endpoint rows already accepted by $\mathsf{ConnCls}$.

Package that comparison as a $\mathsf{BHist}$ boundary row. Since the packet exposes the dependency certificates and provenance rows, $\CurvatureUp$ can read the boundary without adding a new carrier object or quotienting the derivative endpoints.
\end{proof}
\leanchecked{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_curvature\_boundary\_obligation}

\begin{theorem}[Connection stability-ledger exactness obligation]
\label{thm:connection-stability-ledger-exactness-obligation}
The displayed connection surface has exactly the classifier reflexivity, symmetry, and transitivity rows inherited from $\hsame$, $\BundleUp$, and $\ManifoldUp$; the carrier transport rows generated by those classifiers; the ledger readback rows for base, fibre, section, tangent, derivative, and $\mathsf{Pkg}$ provenance; and the exactness rows for section-linearity, parallel transport, and curvature-boundary formation. No additional coordinate chart, host connection operator, or standard bridge row is part of the obligation surface.
\end{theorem}
\leanchecked{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_stability\_ledger\_exactness\_obligation}
\begin{proof}
Classifier stability is componentwise. Reflexivity, symmetry, and transitivity for derivative endpoints come from $\hsame$, while the base, fibre, section, and tangent components are supplied by the two dependency certificates.

Carrier transport follows by applying those componentwise classifier rows to the tuple of \autoref{def:connection-carrier-packet}. Ledger readback is by projection from the tuple: each accepted connection row exposes exactly its base, fibre, section, tangent, derivative endpoint, dependency certificate, and provenance fields.

Exactness is the reverse reading. The section-linearity, parallel-transport, and curvature-boundary obligations use only the projected rows and finite $\Cont$ ledgers already listed above, so any accepted certificate step is one of the displayed connection rows and every displayed row is used by one of those certificate steps.
\end{proof}

\section{The certificate}
\label{sec:connection-certificate}
\closureat{ConnectionUp}{obligationStr}[BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_stability\_ledger\_exactness\_obligation]

\begin{closurestatus}{\ConnectionUp}
  \theoryclosure{\obligationClosure}
  \scopeclosed{The obligation boundary is the displayed carrier packet, the $\mathsf{ConnCls}$ classifier, the section-linearity row, the parallel-transport row, the curvature-boundary row, and the stability-ledger exactness row over $\BundleUp$, $\ManifoldUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.ConnectionUp.ConnectionCarrierPacket\_stability\_ledger\_exactness\_obligation}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Leibniz, coordinate-chart semantics, curvature compatibility, a public bridge, or a standard bridge.}
  \upgradepath{Scoped closure requires binding each obligation row to its exact BEDC dependency scope and downstream $\CurvatureUp$ consumption boundary.}
\end{closurestatus}
