\chapter{A Concrete Naming Certificate for $\AbelUniformUp$}
\label{ch:concrete-instances-abel-uniform-namecert}
\origin{human}

Following Abel's theorem and Bishop--Bridges constructive analysis, the $\AbelUniformUp$ packet records the finite uniform-convergence boundary where RealSeries partial sums are read as RealPowerSeries radial-window data. It consumes the Abel boundary routes of \autoref{ch:concrete-instances-abel-limit-theorem-namecert} and \autoref{ch:concrete-instances-abel-summation-namecert}, the power-series carrier of \autoref{ch:concrete-instances-realpowerseries-namecert}, the series tail package of \autoref{ch:concrete-instances-uniform-convergence-series-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names uniform Abel convergence as displayed finite rows; it is not a quotient equality of series, a selected infinite sum, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[AbelUniform carrier]
\label{def:abel-uniform-carrier}
An $\AbelUniformUp$ carrier is a finite $\BHist$ packet
$$
U=(R,S,P,W,T,Q,E,H,C,L,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the finite radius-window row, listing the dyadic subradius requests and boundary-approach windows inspected by the Abel consumer.
\item $S$ is the $\RealSeriesUp$ partial-sum row whose finite prefixes are being read inside those radius windows.
\item $P$ is the $\RealPowerSeriesUp$ row exposing the same coefficient windows, radius data, and partial-sum reads as power-series data.
\item $W$ is the $\UniformConvergenceSeriesUp$ tail-budget row, assigning a common tail threshold to every displayed radius-window request in $R$.
\item $T$ is the $\AbelSummationUp$ and $\AbelLimitTheoremUp$ boundary row that records the Abel radial handoff after $R,S,P,W$ have been accepted.
\item $Q$ is the $\RegSeqRatUp$ readback row obtained from the synchronized partial-sum and power-series windows.
\item $E$ is the $\RealUp$ seal row exposed only after the Abel boundary row and the regular rational readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the radius, RealSeries, RealPowerSeries, uniform-tail, Abel-boundary, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each Abel uniform request through $R,S,P,W,T,Q,E$.
\item $L$ is the $\Pkg$ provenance over $\AbelUniformUp$, $\AbelLimitTheoremUp$, $\AbelSummationUp$, $\RealSeriesUp$, $\RealPowerSeriesUp$, $\UniformConvergenceSeriesUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\AbelUniformUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $R,S,P,W,T,Q,E,H,C,L,N$. It has no coordinate for selected sums, quotient series equality, countable choice, host power-series equality, ambient completeness, or a Real seal detached from the displayed Abel uniform route.
\end{definition}

\begin{theorem}[AbelUniform NameCert obligations]
\label{thm:abel-uniform-namecert-obligations}
For every accepted $\AbelUniformUp$ carrier
$$
U=(R,S,P,W,T,Q,E,H,C,L,N),
$$
the local $\NameCert_{\AbelUniformUp}$ surface consists exactly of carrier admission for the displayed rows, Abel radius-window monotonicity through $R$, RealSeries and RealPowerSeries partial-sum alignment through $S$ and $P$, uniform-tail exactness through $W$, Abel boundary handoff through $T$, RegSeqRat readback and Real seal nonescape through $Q$ and $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $L$, and local naming through $N$. No obligation row supplies selected sums, quotient series equality, countable choice, host analytic equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:abel-uniform-carrier}. Its mathematical rows are the radius-window row $R$, the $\RealSeriesUp$ partial-sum row $S$, the $\RealPowerSeriesUp$ row $P$, the $\UniformConvergenceSeriesUp$ tail-budget row $W$, the Abel boundary row $T$, the $\RegSeqRatUp$ readback $Q$, and the $\RealUp$ seal $E$.

The radius-window monotonicity is local to $R$. A smaller displayed radius window is read by restricting the same dyadic boundary row, while $S$ and $P$ keep the RealSeries prefix and RealPowerSeries partial-sum read synchronized over that window.

Uniform-tail exactness is supplied by $W$. For each requested tolerance, $W$ gives one tail threshold shared by every displayed radius-window row, so the Abel boundary read in $T$ cannot choose a separate threshold for each point of the window.

The readback and seal rows are downstream. The row $Q$ repacks the accepted synchronized windows as regular rational data, and $E$ exposes the terminal Real seal only after $R,S,P,W,T,Q$ have been read.

Finally $H,C,L,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for selected sums, quotient series equality, countable choice, host analytic equality, or ambient completeness, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[AbelUniform boundary consumer route]
\label{thm:abel-uniform-boundary-consumer-route}
Every RealPowerSeries or RealSeries consumer of an accepted $\AbelUniformUp$ packet factors through
$$
\RealSeriesUp \longmapsto \RealPowerSeriesUp \longmapsto \UniformConvergenceSeriesUp \longmapsto \AbelSummationUp/\AbelLimitTheoremUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
inside the same finite radius-window package. The consumer receives no selected sum, quotient equality of series, countable-choice schedule, host boundary-limit theorem, or ambient $\RealUp$ completeness claim.
\end{theorem}
\begin{proof}
Start with the RealSeries and RealPowerSeries rows $S$ and $P$. They name the same finite partial-sum windows, first as series-prefix data and then as radius-window power-series data.

Apply the uniform-tail row $W$. It supplies the shared threshold discipline needed by $\UniformConvergenceSeriesUp$, so a boundary consumer cannot vary the tail budget independently across the displayed radius window.

Now read the Abel boundary row $T$. The sibling $\AbelSummationUp$ and $\AbelLimitTheoremUp$ routes are consumed only after $R,S,P,W$ have fixed the finite radial surface.

The route then passes through $\RegSeqRatUp$ readback $Q$ and terminal $\RealUp$ seal $E$, with $H,C,L,N$ preserving the same packet. Because the refused host and quotient objects are absent from the carrier, every boundary consumer remains inside the displayed route.
\end{proof}

\falsifiablePrediction{Every accepted $\AbelUniformUp$ boundary read exposes a radius-window row, RealSeries partial-sum row, RealPowerSeries row, UniformConvergenceSeries tail budget, Abel boundary row, RegSeqRat readback, RealUp seal, componentwise transport, displayed replay, provenance, and local NameCert before a Real-facing consumer can inspect the endpoint.}

\independenceWitness{abel-limit-theorem, abel-summation, realpowerseries, uniform-convergence-series, regseqrat, real: none is bijective to $\AbelUniformUp$ because this packet jointly carries radius-window monotonicity, RealSeries and RealPowerSeries partial-sum alignment, one uniform tail budget, Abel boundary handoff, regular rational readback, terminal real sealing, transport, replay, provenance, and local naming.}

\closureat{AbelUniformUp}{seedStr}

\begin{closurestatus}{\AbelUniformUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:abel-uniform-carrier}, \autoref{thm:abel-uniform-namecert-obligations}, and \autoref{thm:abel-uniform-boundary-consumer-route} seed the finite uniform Abel boundary over radius windows, RealSeries partial sums, RealPowerSeries rows, UniformConvergenceSeries tail budgets, RegSeqRat readback, and the RealUp seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected sums, quotient equality of series, countable choice, host analytic equality, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, radius-window monotonicity, partial-sum alignment, uniform-tail exactness, Abel boundary handoff, readback, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.AbelUniformUp.}
  \constructivestory{An $\AbelUniformUp$ packet is generated from radius-window rows, RealSeries partial sums, RealPowerSeries rows, UniformConvergenceSeries tail budgets, AbelSummation and AbelLimitTheorem boundary rows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
