\chapter{A Concrete Naming Certificate for $\BishopCompletionSpaceUp$}
\label{ch:concrete-instances-bishop-completion-space-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopCompletionSpaceUp$ packet records the constructive completion-space interface as finite BEDC NameCert data. It sits after the stream-name carrier of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the Cauchy-filter completion packet of \autoref{ch:concrete-instances-cauchyfiltercompletion-namecert}. The packet names the completion-space rows consumed by real and metric completion arguments; it does not assert ambient completeness, quotient equality of Cauchy objects, selected limits, countable choice, or a host completion theorem.

\begin{definition}[Bishop completion-space carrier]
\label{def:bishop-completion-space-carrier}
A $\BishopCompletionSpaceUp$ carrier is a finite $\BHist$ packet
$$
S=(X,Q,D,R,E,F,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source-space row, recording the displayed carrier, apartness or metric-facing classifier, and finite observation route used by the completion request.
\item $Q$ is the regular Cauchy-name row, read through $\StreamNameUp$ and the lawlike finite windows visible to the packet.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger that bounds the inspected Cauchy windows.
\item $R$ is the $\RegSeqRatUp$ readback row produced by the finite Cauchy data.
\item $E$ is the $\RealUp$ seal row consumed only after $Q,D,R$ have been displayed.
\item $F$ is the $\CauchyFilterCompletionUp$ face recording how the same Cauchy data enters the completion-facing filter route.
\item $H$ records componentwise $\hsame$ transport for the source, Cauchy-name, dyadic tolerance, regular readback, Real seal, filter-completion face, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
X,Q,D \longmapsto R \longmapsto E
\qquad\text{and}\qquad
X,Q,D \longmapsto F .
$$
\item $P$ is the $\Pkg$ provenance over $\BishopCompletionSpaceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CauchyFilterCompletionUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCompletionSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $X,Q,D,R,E,F,H,C,P,N$. It has no coordinate for quotient equality of Cauchy names, selected limits, ambient completeness, countable choice, host real equality, or an unrestricted completion object.
\end{definition}

\begin{theorem}[Bishop completion-space NameCert obligations]
\label{thm:bishop-completion-space-namecert-obligations}
For every accepted $\BishopCompletionSpaceUp$ carrier $S=(X,Q,D,R,E,F,H,C,P,N)$, the local $\NameCert_{\BishopCompletionSpaceUp}$ surface consists exactly of source-space exposure through $X$, regular Cauchy-name exposure through $Q$, dyadic tolerance exposure through $D$, regular rational readback through $R$, Real seal handoff through $E$, Cauchy-filter completion exposure through $F$, componentwise transport through $H$, displayed continuation replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The source row $X$, Cauchy-name row $Q$, dyadic tolerance ledger $D$, regular readback $R$, Real seal $E$, and filter-completion face $F$ are the only completion-facing data admitted by the packet.

The analytic obligations are therefore finite. A completion consumer must first display the source row and inspected Cauchy windows, then the dyadic tolerance ledger, then the regular rational readback and Real seal. The filter-completion face is read from the same displayed data and does not add a second completion object.

The structural obligations are componentwise transport, replay, provenance, and local naming. Since the carrier has no coordinate for quotient Cauchy equality, selected limits, ambient completeness, countable choice, host real equality, or an unrestricted completion object, the listed rows exhaust the NameCert surface.
\end{proof}

\begin{theorem}[Bishop completion-space Real route]
\label{thm:bishop-completion-space-real-route}
Every real-facing or completion-facing consumer of an accepted $\BishopCompletionSpaceUp$ packet factors through the displayed route
$$
\StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp,\ \CauchyFilterCompletionUp
$$
by reading $X,Q,D,R,E,F,H,C,P,N$. The route exports finite Cauchy, regular-rational, Real-seal, and filter-completion rows; it exports no quotient equality, selected limit, ambient complete space, countable-choice principle, or hidden host completion.
\end{theorem}
\begin{proof}
Begin with the stream-name and Cauchy-window rows. The row $Q$ is read only as displayed finite windows over the source row $X$, and the tolerance ledger $D$ bounds those windows before any real-facing readback is public.

Next read the regular rational and Real rows. The row $R$ exposes the regular rational name, and $E$ seals it as a $\RealUp$ row only after $X,Q,D$ have been displayed.

Finally read the completion face. The row $F$ records the Cauchy-filter completion handoff over the same finite data, while $H,C,P,N$ preserve transport, replay, provenance, and local naming. Thus every consumer receives the finite Bishop completion-space route and none of the excluded host objects.
\end{proof}

\falsifiablePrediction{Every $\BishopCompletionSpaceUp$ read must expose source-space, StreamName, dyadic tolerance, RegSeqRat readback, Real seal, CauchyFilterCompletion, hsame transport, Cont replay, Pkg provenance, and local NameCert rows before a completion-facing conclusion is consumed.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, cauchyfiltercompletion: $\BishopCompletionSpaceUp$ is not bijective to any listed sibling because it jointly carries source-space exposure, regular Cauchy windows, dyadic tolerance, regular rational readback, Real seal, Cauchy-filter completion face, transport, replay, provenance, and local naming in one completion-space packet.}

\closureat{BishopCompletionSpaceUp}{seedStr}

\begin{closurestatus}{\BishopCompletionSpaceUp}
  \constructivestory{A $\BishopCompletionSpaceUp$ packet is generated from a source-space row, regular Cauchy-name row, dyadic tolerance ledger, RegSeqRat readback, Real seal, CauchyFilterCompletion face, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-completion-space-carrier}, \autoref{thm:bishop-completion-space-namecert-obligations}, and \autoref{thm:bishop-completion-space-real-route} seed the finite constructive completion-space interface over stream-name, regular rational, dyadic tolerance, Real-seal, and Cauchy-filter completion rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim ambient completeness, quotient equality of Cauchy names, selected limits, countable choice, host real equality, Lean verification, bridge checking, or an unrestricted completion theorem.}
  \upgradepath{Obligation closure requires checked carrier admission, Cauchy-window exposure, dyadic tolerance exactness, regular rational readback, Real-seal nonescape, Cauchy-filter completion compatibility, transport, replay, provenance, and local naming for BEDC.Derived.BishopCompletionSpaceUp.}
\end{closurestatus}
