\chapter{A Concrete Naming Certificate for $\CauchyBornologyBasisUp$}
\label{ch:concrete-instances-cauchy-bornology-basis-namecert}
\origin{human}

Following Bishop and Bridges on constructive completion and Bourbaki/Kelley on bornologies, the $\CauchyBornologyBasisUp$ packet records the finite basis-level route by which Cauchy filter observations, boundedness control, metric boundedness, stream windows, rational readback, dyadic tolerances, and the terminal real seal are exposed before a completion-facing consumer may act. It sits between the Cauchy bornology of \autoref{ch:concrete-instances-cauchy-bornology-namecert}, the finite Cauchy filter basis of \autoref{ch:concrete-instances-cauchy-filter-basis-namecert}, the metric bornology of \autoref{ch:concrete-instances-metric-bornology-namecert}, the located Cauchy filter basis of \autoref{ch:concrete-instances-located-cauchy-filter-basis-namecert}, the stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names the basis-bornology bridge needed by Real and Completion routes; it does not quotient filters, select limits, use countable choice, or assume ambient $\RealUp$ completeness.

\begin{definition}[Cauchy bornology basis carrier]
\label{def:cauchy-bornology-basis-carrier}
A $\CauchyBornologyBasisUp$ carrier is a finite $\BHist$ packet
$$
B=(F,G,M,S,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\CauchyFilterBasisUp$ row, exposing finite basic filter requests, directed refinements, and Cauchy-pressure witnesses.
\item $G$ is the $\CauchyBornologyUp$ row, recording which displayed Cauchy-filter requests are bounded in the bornological sense.
\item $M$ is the $\MetricBornologyUp$ row, tying the boundedness read to a metric-ball or diameter ledger rather than to host-set inclusion.
\item $S$ is the $\StreamNameUp$ finite-window service used to inspect the requested basis entries.
\item $W$ is the window-boundedness row, matching the displayed stream windows with the bornology rows $G,M$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to those windows and boundedness reads.
\item $R$ is the $\RegSeqRatUp$ regular rational readback available only after $F,G,M,S,W,D$ have been displayed.
\item $E$ is the terminal $\RealUp$ seal reached only through the displayed basis-bornology route.
\item $H$ records componentwise $\hsame$ transport for all basis, bornology, metric, window, tolerance, readback, seal, exactness, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the same route.
\item $P$ is the $\Pkg$ provenance over $\CauchyBornologyBasisUp$, $\CauchyFilterBasisUp$, $\CauchyBornologyUp$, $\MetricBornologyUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyBornologyBasisUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,G,M,S,W,D,R,E,H,C,P,N$. It has no coordinate for quotient filters, selected limits, countable choice, host bounded-set equality, hidden Cauchy representatives, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Cauchy bornology basis NameCert obligations]
\label{thm:cauchy-bornology-basis-namecert-obligations}
For every accepted $\CauchyBornologyBasisUp$ carrier
$$
B=(F,G,M,S,W,D,R,E,H,C,P,N),
$$
the local $\NameCert_{\CauchyBornologyBasisUp}$ surface consists exactly of the following five obligation rows:
\begin{enumerate}
\item carrier admission for the $\CauchyFilterBasisUp$ row, $\CauchyBornologyUp$ row, $\MetricBornologyUp$ row, $\StreamNameUp$ windows, window-boundedness row, $\DyadicRatCoreUp$ tolerance ledger, $\RegSeqRatUp$ readback, $\RealUp$ seal, transport, replay, provenance, and local naming rows;
\item basis-bornology compatibility, requiring every boundedness read in $G$ to be attached to a displayed finite basis request from $F$;
\item metric boundedness stability, requiring $M$ and $W$ to witness the same bounded window before $D,R,E$ are consumed;
\item completion-route nonescape, excluding quotient filters, selected limits, countable choice, host bounded-set equality, hidden Cauchy representatives, and ambient real completeness from the packet;
\item structural persistence through componentwise $\hsame$, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row $N$.
\end{enumerate}
No other NameCert obligation is available from the Cauchy bornology basis packet.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-bornology-basis-carrier}. Its analytic rows are exactly the Cauchy filter basis, Cauchy bornology row, metric bornology row, stream-window service, window-boundedness row, dyadic tolerance ledger, regular rational readback, and terminal real seal.

The first three obligation rows separate admission from compatibility. Carrier admission displays every coordinate. Basis-bornology compatibility ties $G$ to the finite basis requests in $F$, and metric boundedness stability forces $M$ and $W$ to describe the same visible bounded windows before the tolerance and readback rows are public.

The completion-route nonescape row follows from the same inventory. Since no quotient filter, selected limit, countable-choice schedule, host bounded-set equality, hidden Cauchy representative, or ambient completeness coordinate appears in $B$, none can discharge a local obligation.

Finally $H,C,P,N$ preserve the displayed rows by transport, replay, provenance, and naming. The five rows therefore exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy bornology basis filter handoff]
\label{thm:cauchy-bornology-basis-filter-handoff}
Every completion-facing consumer of an accepted $\CauchyBornologyBasisUp$ carrier reads the finite route
$$
\CauchyFilterBasisUp,\ \CauchyBornologyUp,\ \MetricBornologyUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp
$$
before it can consume the terminal $\RealUp$ seal. The handoff exports only $F,G,M,S,W,D,R,E,H,C,P,N$ and refuses quotient filters, selected representatives, countable choice, host bounded-set equality, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with a completion-facing read of $B$. The only filter source available to the consumer is the displayed basis row $F$, and the only bornological controls are $G$ and $M$.

The consumer must next inspect finite windows. The rows $S$ and $W$ display the requested window and its boundedness read, while $D$ records the dyadic tolerance ledger tied to the same visible data.

Only after this route is displayed may $R$ supply regular rational readback and $E$ supply the terminal real seal. The structural rows $H,C,P,N$ transport, replay, source, and name that same route rather than adding a quotient filter or selected representative.

Thus the handoff is exactly the finite basis-bornology route listed in the statement, and it has no place for countable choice, host bounded-set equality, or ambient real completeness.
\end{proof}

\begin{theorem}[Cauchy bornology basis Real completion boundary]
\label{thm:cauchy-bornology-basis-real-completion-boundary}
An accepted $\CauchyBornologyBasisUp$ packet reaches a Real and Completion boundary only through the displayed rows $F,G,M,S,W,D,R,E,H,C,P,N$. In particular the terminal $\RealUp$ seal $E$ is downstream of the finite Cauchy filter basis, bornology, metric bornology, stream-window, dyadic tolerance, and regular rational readback rows, and no quotient filter, selected limit, countable-choice selector, detached completion object, or ambient $\RealUp$ completeness row can be inserted before $E$.
\end{theorem}
\begin{proof}
Use \autoref{thm:cauchy-bornology-basis-namecert-obligations}. It identifies the complete local certificate surface and shows that the terminal seal is part of the same finite packet as the basis, bornology, metric, window, tolerance, and readback rows.

Now apply the filter handoff theorem, \autoref{thm:cauchy-bornology-basis-filter-handoff}. Every completion-facing read reaches $E$ only after $F,G,M,S,W,D,R$ have been displayed and after the structural rows have replayed the same route.

The excluded objects have no carrier coordinate. A quotient filter, selected limit, countable-choice selector, detached completion object, or ambient completeness row would have to enter between $R$ and $E$ or replace one of the displayed support rows, but the packet exposes neither insertion point.
\end{proof}

\falsifiablePrediction{Every accepted $\CauchyBornologyBasisUp$ read that reaches a $\RealUp$ seal must display a CauchyFilterBasis row, a CauchyBornology row, a MetricBornology row, StreamName windows, a window-boundedness row, a DyadicRatCore tolerance ledger, RegSeqRat readback, hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}

\independenceWitness{cauchy-filter-basis, cauchy-bornology, metric-bornology, located-cauchy-filter-basis, streamname, dyadicratcore, regseqrat, real: $\CauchyBornologyBasisUp$ binds finite filter-basis requests, bornological boundedness, metric boundedness, stream-window inspection, dyadic tolerance, regular rational readback, a Real seal, transport, replay, provenance, and local naming in one basis-level packet; each listed sibling lacks at least one of these rows as a local completion-facing coordinate.}

\closureat{CauchyBornologyBasisUp}{seedStr}

\begin{closurestatus}{\CauchyBornologyBasisUp}
  \constructivestory{A $\CauchyBornologyBasisUp$ packet is generated from a CauchyFilterBasis row, a CauchyBornology row, a MetricBornology row, StreamName windows, a window-boundedness row, DyadicRatCore tolerance data, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-bornology-basis-carrier}, \autoref{thm:cauchy-bornology-basis-namecert-obligations}, \autoref{thm:cauchy-bornology-basis-filter-handoff}, and \autoref{thm:cauchy-bornology-basis-real-completion-boundary} seed the finite basis-bornology route for Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient filters, selected representatives, selected limits, countable choice, host bounded-set equality, detached completion objects, ambient $\RealUp$ completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, basis-bornology compatibility, metric boundedness stability, filter handoff, Real completion boundary nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CauchyBornologyBasisUp.}
\end{closurestatus}
