\chapter{A Concrete Naming Certificate for $\RegularCauchyApartnessReflectorUp$}
\label{ch:concrete-instances-regular-cauchy-apartness-reflector-namecert}
\origin{human}

Following Bishop and Bridges, the $\RegularCauchyApartnessReflectorUp$ packet records the finite handoff from regular Cauchy name data to located apartness reads. It sits after the stream-name surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational sequence surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the located-real surface of \autoref{ch:concrete-instances-located-real-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the Bishop located-real completion route of \autoref{ch:concrete-instances-bishop-located-real-completion-namecert}. The packet exposes apartness as inspected finite NameCert data; it does not import trichotomy, quotient stream equality, selected limits, or ambient $\RealUp$ completeness.

\begin{definition}[Regular Cauchy apartness reflector carrier]
\label{def:regular-cauchy-apartness-reflector-carrier}
A $\RegularCauchyApartnessReflectorUp$ carrier is a finite $\BHist$ packet
$$
K=(S,R,D,A,L,E,H,C,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ finite-window row, naming the inspected source positions and readback order.
\item $R$ is the $\RegSeqRatUp$ regular rational source row whose accepted windows are being compared.
\item $D$ is the $\DyadicRatCoreUp$ tolerance and positive-gap ledger used by the apartness read.
\item $A$ is the displayed apartness row, recording the finite positive separation evidence accepted for the same regular Cauchy windows.
\item $L$ is the $\LocatedRealUp$ handoff row, exposing the located read reached from $S,R,D,A$.
\item $E$ is the terminal $\RealUp$ seal row reached only after the located-real handoff has been displayed.
\item $H$ records componentwise $\hsame$ transport for $S,R,D,A,L,E$.
\item $C$ records displayed $\Cont$ replay from regular Cauchy windows through dyadic positive-gap evidence, located-real handoff, and the Real seal.
\item $N$ is both the $\Pkg$ provenance over the listed BEDC dependencies and the local $\NameCert_{\RegularCauchyApartnessReflectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,R,D,A,L,E,H,C,N$. It has no coordinate for trichotomy, quotient stream equality, selected limit representatives, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Regular Cauchy apartness reflector NameCert obligations]
\label{thm:regular-cauchy-apartness-reflector-namecert-obligations}
For every accepted $\RegularCauchyApartnessReflectorUp$ carrier
$$
K=(S,R,D,A,L,E,H,C,N),
$$
the local $\NameCert_{\RegularCauchyApartnessReflectorUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the stream windows, regular rational source, dyadic positive-gap ledger, apartness row, located-real handoff, Real seal, transport, replay, provenance, and local name;
\item window and readback exactness, requiring the read through $S$ and $R$ to be the same finite regular Cauchy window consumed by the apartness row;
\item apartness-row exposure, requiring every accepted positive separation read to pass through $A$ after the dyadic ledger $D$ has been displayed;
\item located-real handoff, requiring the row $L$ to be reached only from $S,R,D,A$;
\item Real-seal nonescape, requiring $E$ to expose only the terminal seal after the located-real handoff;
\item transport, replay, provenance, and local naming, requiring $H,C,N$ to preserve and name the same displayed route.
\end{enumerate}
No obligation supplies trichotomy, quotient stream equality, selected limits, host equality, or ambient $\RealUp$ completeness outside these rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-apartness-reflector-carrier}. The displayed tuple $S,R,D,A,L,E,H,C,N$ is the entire public surface, so carrier admission is admission of those rows.

Window and readback exactness are forced by the order of the tuple. The stream-name row $S$ fixes the inspected windows, and the regular rational row $R$ fixes the rational readback on those windows before any apartness row is available.

The apartness-row exposure is the joint role of $D$ and $A$. The dyadic ledger supplies the positive-gap cells, while $A$ records the accepted finite apartness read over those same cells.

The located-real handoff and Real seal are downstream rows. The handoff $L$ can be read only after $S,R,D,A$, and the seal $E$ can be read only after $L$ has been displayed.

Finally, $H,C,N$ transport, replay, source, and name the same route. Since the excluded objects are absent as carrier coordinates, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Regular Cauchy apartness located-real handoff]
\label{thm:regular-cauchy-apartness-reflector-located-real-handoff}
Let $K=(S,R,D,A,L,E,H,C,N)$ be an accepted $\RegularCauchyApartnessReflectorUp$ carrier. Every accepted apartness read from $A$ passes through the finite route
$$
\StreamNameUp\longmapsto\RegSeqRatUp\longmapsto\DyadicRatCoreUp\longmapsto\LocatedRealUp\longmapsto\RealUp
$$
as witnessed by the rows $S,R,D,L,E$ of the same packet, with $H,C,N$ carrying only transport, replay, provenance, and local naming for that route.
\end{theorem}
\begin{proof}
Start with an accepted apartness read from $A$. By the carrier definition, the only inspected source windows available to that read are named by $S$.

The regular rational readback row $R$ is then the only source of rational observations on those windows. The positive-gap evidence for apartness must next be read through the dyadic ledger $D$, so the apartness row is not a detached order comparison or a trichotomy branch.

The located-real row $L$ consumes exactly the displayed stream, regular rational, dyadic, and apartness rows. Thus the handoff is a located-real read, not a quotient-stream equality or selected representative.

After $L$ is displayed, the terminal row $E$ seals the same read as a $\RealUp$ name. The structural rows $H,C,N$ preserve, replay, source, and name the route without adding ambient completeness, so every accepted apartness read passes through the displayed finite handoff.
\end{proof}

\begin{closurestatus}{\RegularCauchyApartnessReflectorUp}
  \constructivestory{A $\RegularCauchyApartnessReflectorUp$ packet is generated from StreamName finite windows, RegSeqRat regular rational readback, DyadicRatCore positive-gap evidence, an apartness row, a LocatedReal handoff, a Real seal, componentwise hsame transport, displayed Cont replay, provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-apartness-reflector-carrier}, \autoref{thm:regular-cauchy-apartness-reflector-namecert-obligations}, and \autoref{thm:regular-cauchy-apartness-reflector-located-real-handoff} seed the finite apartness-reflection route from regular Cauchy windows through dyadic positive-gap evidence, located-real handoff, Real seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close trichotomy, quotient stream equality, selected limit representatives, host equality, ambient $\RealUp$ completeness, Lean theorem checking, or bridge checking for $\RegularCauchyApartnessReflectorUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, window and readback exactness, apartness-row exposure, located-real handoff, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchyApartnessReflectorUp.}
\end{closurestatus}
\leanstmt{BEDC.Derived.RegularCauchyApartnessReflectorUp}
