\chapter{A Concrete Naming Certificate for $\RiemannIntegralCompletionModulusUp$}
\label{ch:concrete-instances-riemann-integral-completion-modulus-namecert}
\origin{human}

Following Riemann and Bishop--Bridges constructive integration, the $\RiemannIntegralCompletionModulusUp$ packet records the finite modulus route by which integration evidence becomes regular-rational and real-name readback data. It sits after the Darboux-gap evidence of \autoref{ch:concrete-instances-riemann-integrable-namecert}, the tagged-gauge window surface of \autoref{ch:concrete-instances-riemann-sum-gauge-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the reusable finite interface between integrability evidence and completion-facing reads; it does not supply a host limit, quotient equality of integrands, selected partitions, measure completion, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Riemann integral completion-modulus carrier]
\label{def:riemann-integral-completion-modulus-carrier}
A $\RiemannIntegralCompletionModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(I,G,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\RiemannIntegrableUp$ row carrying Darboux-gap evidence for the inspected integrand and interval.
\item $G$ is the $\RiemannSumGaugeUp$ row carrying tagged windows, gauge radii, mesh comparisons, and finite Riemann-sum reads.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row that records the displayed precision request, comparison slack, and dyadic bound used by the completion-facing read.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed integrability, tagged-gauge, and dyadic tolerance rows.
\item $E$ is the terminal $\RealUp$ seal reached only after the regular-rational readback row is public.
\item $H$ records componentwise $\hsame$ transport for the integrability row, tagged-gauge row, dyadic tolerance row, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the integrability evidence through tagged windows, dyadic tolerance, regular readback, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\RiemannIntegralCompletionModulusUp$, $\RiemannIntegrableUp$, $\RiemannSumGaugeUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RiemannIntegralCompletionModulusUp}$ row.
\end{enumerate}
The classifier reads accepted carriers only through $I,G,D,R,E,H,C,P,N$. It has no coordinate for host limits, quotient equality of integrands, selected partition families, measure completion, countable choice, detached integral representatives, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Riemann integral completion-modulus NameCert obligations]
\label{thm:riemann-integral-completion-modulus-obligations}
For every accepted carrier
$$
M=(I,G,D,R,E,H,C,P,N)
$$
of \autoref{def:riemann-integral-completion-modulus-carrier}, the local $\NameCert_{\RiemannIntegralCompletionModulusUp}$ surface consists exactly of carrier admission for the $\RiemannIntegrableUp$ gap row, $\RiemannSumGaugeUp$ tagged-window row, $\DyadicRatCoreUp$ tolerance row, $\RegSeqRatUp$ readback row, $\RealUp$ seal, transport, replay, provenance, and local naming; gap-to-window compatibility requiring $G$ to read the integrability evidence displayed by $I$; tolerance exactness requiring $D$ to mediate every completion-facing precision request before $R$ is read; Real-seal compatibility requiring $E$ to be downstream of $R$; and nonescape excluding host limits, quotient integrand equality, selected partition families, measure completion, countable choice, detached integral representatives, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:riemann-integral-completion-modulus-carrier}. The packet displays exactly one integrability row, one tagged-gauge row, one dyadic tolerance row, one regular-rational readback, one Real seal, and the structural rows.

Gap-to-window compatibility is read from $I$ and $G$. The integrability row supplies the finite Darboux-gap evidence, while the tagged-gauge row supplies only the windows and mesh comparisons attached to that evidence.

Tolerance exactness is the role of $D$. A completion-facing precision request reaches the regular readback row $R$ only after the dyadic bound and comparison slack have been displayed.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name the same finite route. Since the carrier omits host limits, quotient integrand equality, selected partition families, measure completion, countable choice, detached representatives, and ambient completeness, the listed clauses exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Riemann integral completion-modulus handoff]
\label{thm:riemann-integral-completion-modulus-handoff}
Every completion-facing integration read of an accepted $\RiemannIntegralCompletionModulusUp$ carrier factors through the displayed route
$$
\RiemannIntegrableUp \longmapsto \RiemannSumGaugeUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
Thus the read exports only the finite rows $I,G,D,R,E,H,C,P,N$ and cannot export a host limit, quotient equality of integrands, selected partition family, measure completion, countable choice, detached integral representative, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a completion-facing integration read. The only source row available to it is the integrability row $I$, which displays Darboux-gap evidence before any tagged window or regular readback is inspected.

The next analytic row is $G$. It exposes tagged windows, gauge radii, mesh comparisons, and finite Riemann-sum reads, but it does not select a partition family or identify integrands by quotient equality.

The dyadic row $D$ then mediates the precision request. Only after this displayed tolerance read may the carrier expose the $\RegSeqRatUp$ row $R$ and the terminal $\RealUp$ seal $E$.

Transport, replay, provenance, and local naming preserve the same order through $H,C,P,N$. Because no omitted object is present as a carrier coordinate, every accepted completion-facing read factors through the displayed finite route and exports nothing beyond it.
\end{proof}

\closureat{RiemannIntegralCompletionModulusUp}{seedStr}

\begin{closurestatus}{\RiemannIntegralCompletionModulusUp}
  \constructivestory{A $\RiemannIntegralCompletionModulusUp$ packet is generated from a RiemannIntegrableUp Darboux-gap row, a RiemannSumGaugeUp tagged-window row, a DyadicRatCoreUp tolerance row, RegSeqRatUp readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:riemann-integral-completion-modulus-carrier}, \autoref{thm:riemann-integral-completion-modulus-obligations}, and \autoref{thm:riemann-integral-completion-modulus-handoff} seed the finite integration-modulus route from integrability evidence through tagged windows, dyadic tolerance, regular readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host limits, quotient equality of integrands, selected partition families, measure completion, countable choice, detached integral representatives, ambient $\RealUp$ completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, gap-to-window compatibility, tolerance exactness, RegSeqRat readback, Real-seal compatibility, transport, replay, provenance, and local naming for BEDC.Derived.RiemannIntegralCompletionModulusUp.}
\end{closurestatus}
