\chapter{A Concrete Naming Certificate for $\BoundaryFarEndNoncenterUp$}
\label{ch:concrete-instances-boundary-far-end-noncenter-namecert}
\origin{ai}

The $\BoundaryFarEndNoncenterUp$ packet realizes the boundary-fixedness-not-center rule of \autoref{prin:hyperbolic-boundary-not-center} as finite NameCert data. It sits beside the Poincare disk dynamics packet of \autoref{ch:concrete-instances-poincare-disk-dynamics-namecert}, the hyperbolic geodesic boundary packet of \autoref{ch:concrete-instances-hyperbolic-geodesic-boundary-namecert}, the hyperbolic visual boundary packet of \autoref{ch:concrete-instances-hyperbolic-visual-boundary-namecert}, the apophatic far-end socket packet, and the circle boundary reading. The packet names a displayed boundary far-end refusal; it does not identify the far end with an interior disk center or with a hidden global object.

\begin{definition}[Boundary far-end noncenter carrier]
\label{def:boundary-far-end-noncenter-carrier}
A $\BoundaryFarEndNoncenterUp$ carrier is a finite $\BHist$ packet
$$
Q=(D,B,F,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the disk/readout row, recording the visible disk surface and the inspected readout whose center interpretation is being tested.
\item $B$ is the boundary far-end row, displaying the boundary-side far-end reading rather than an interior point.
\item $F$ is the fixedness row, recording that fixedness is read at the boundary far end and not at the disk center.
\item $A$ is the apophatic refusal row, refusing any consumer that converts boundary far-end data into center data or object-level $\mathsf{T}$.
\item $H$ records componentwise $\hsame$ transport for $D,B,F,A$.
\item $C$ records displayed $\Cont$ replay from disk readout through boundary far-end fixedness and apophatic refusal.
\item $P$ is the $\Pkg$ provenance over $\BoundaryFarEndNoncenterUp$, the hyperbolic boundary route, apophatic far-end discipline, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BoundaryFarEndNoncenterUp}$ row.
\end{enumerate}
The carrier has no coordinate for a privileged disk center, a selected ideal point, a quotient boundary equality, subject-substance, or object-level $\mathsf{T}$ outside the displayed refusal row.
\end{definition}

\begin{theorem}[Boundary far-end noncenter obligations]
\label{thm:boundary-far-end-noncenter-obligations}
For every accepted $\BoundaryFarEndNoncenterUp$ carrier $Q=(D,B,F,A,H,C,P,N)$, the local $\NameCert_{\BoundaryFarEndNoncenterUp}$ surface consists exactly of carrier admission for the displayed disk/readout, boundary far-end, fixedness, apophatic refusal, transport, replay, provenance, and local naming rows; fixedness exactness through $F$; refusal visibility through $A$; and noncenter refusal for any read that treats $D$ as carrying the boundary far end through an interior center.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:boundary-far-end-noncenter-carrier}. The disk/readout row $D$ names only the visible surface and inspected readout, while $B$ names the boundary far-end row.

The fixedness row $F$ is tied to $B$, not to an interior center coordinate in $D$. The refusal row $A$ is therefore part of the certificate surface: a consumer that reads fixedness as center data has not displayed the accepted packet.

The rows $H,C,P,N$ transport, replay, source, and name the same finite data. Thus the listed rows exhaust the local NameCert obligations, and no hidden center, selected ideal point, quotient boundary equality, subject-substance, or object-level $\mathsf{T}$ can enter the accepted route.
\end{proof}

\begin{theorem}[Boundary far-end fixedness noncenter rule]
\label{thm:boundary-far-end-noncenter-fixedness}
For every accepted $\BoundaryFarEndNoncenterUp$ carrier $Q=(D,B,F,A,H,C,P,N)$, boundary fixedness is read only from the displayed boundary far-end row $B$ together with the fixedness row $F$. Any disk-center reading of $D$ that bypasses the apophatic refusal row $A$ is not a consumer of the same packet.
\end{theorem}
\begin{proof}
The carrier separates the visible disk/readout row $D$ from the boundary far-end row $B$. The fixedness row $F$ is attached to $B$, while $A$ records the refusal of center collapse.

If a consumer bypasses $A$, it has removed the row that distinguishes boundary far-end data from center data. If it reads $D$ as the fixed far end, it has replaced the boundary row by an interior readout. In both cases the displayed packet is not preserved, so the consumer is outside $\BoundaryFarEndNoncenterUp$.
\end{proof}

\falsifiablePrediction{Every accepted $\BoundaryFarEndNoncenterUp$ consumer must display the boundary far-end row and apophatic refusal row before any disk-center read is rejected as noncenter data.}

\independenceWitness{poincare-disk-dynamics, hyperbolic-geodesic-boundary, hyperbolic-visual-boundary, apophaticfarendsocket, and s1: none carries the same boundary/noncenter/refusal rows. The dynamics packet exposes disk-map evolution, the geodesic and visual boundary packets expose boundary routes, the far-end socket exposes apophatic pressure, and s1 exposes a circle boundary shape; only $\BoundaryFarEndNoncenterUp$ binds disk readout, boundary far-end fixedness, noncenter refusal, transport, replay, provenance, and local naming in one packet.}

The Lean follow-up file \texttt{lean4/BEDC/Derived/BoundaryFarEndNoncenterUp/TasteGate.lean} must provide explicit $\mathsf{Nontrivial}\ \BoundaryFarEndNoncenterUp$ and $\mathsf{FieldFaithful}\ \BoundaryFarEndNoncenterUp$ instances preserving $D,B,F,A,H,C,P,N$ before any checked carrier-alignment theorem can serve as a TasteGate realization.

\begin{closurestatus}{\BoundaryFarEndNoncenterUp}
  \constructivestory{A $\BoundaryFarEndNoncenterUp$ packet is generated from disk/readout rows, boundary far-end rows, boundary fixedness rows, apophatic refusal rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:boundary-far-end-noncenter-carrier}, \autoref{thm:boundary-far-end-noncenter-obligations}, \autoref{thm:boundary-far-end-noncenter-fixedness}, the falsifiable prediction, and the independence witness seed the finite boundary-far-end noncenter packet over disk readout, boundary far-end fixedness, refusal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close privileged disk centers, selected ideal points, quotient boundary equality, subject-substance, object-level $\mathsf{T}$, Lean verification, or bridge checking for $\BoundaryFarEndNoncenterUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, boundary fixedness exactness, apophatic refusal visibility, noncenter refusal, transport, replay, provenance, local naming, and TasteGate Nontrivial and FieldFaithful instances for BEDC.Derived.BoundaryFarEndNoncenterUp.}
\end{closurestatus}
