\chapter{A Concrete Naming Certificate for $\ClusterFilterUp$}
\label{ch:concrete-instances-cluster-filter-namecert}
\origin{human}

Following Kelley, Bourbaki, and Bishop-style filter convergence, the $\ClusterFilterUp$ packet records the finite interface by which a displayed filter base can be read as clustering around a point or completion boundary. It sits after the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the metric-space carrier of \autoref{ch:concrete-instances-metric-space-namecert}, the topology carrier of \autoref{ch:concrete-instances-topology-namecert}, the finite stream-name route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter supplies a standard cluster-filter neighbor for completion and compactness arguments without importing host powersets, selected adherent points, quotient filters, countable choice, or ambient completeness.

\begin{definition}[ClusterFilter carrier]
\label{def:cluster-filter-carrier}
A $\ClusterFilterUp$ carrier is a finite $\BHist$ packet
$$
G=(F,M,T,W,R,E,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the visible $\CauchyFilterUp$ row naming the finite filter-base requests, directed refinements, and Cauchy-readiness data that may be inspected by a completion consumer.
\item $M$ is the $\MetricSpaceUp$ row recording the distance observations and metric-law ledger used by every ball-neighborhood request.
\item $T$ is the $\TopologyUp$ row recording the neighbourhood reads through which clustering is observed.
\item $W$ is the $\StreamNameUp$ finite-window row used when the filter is probed by sequential or net-shaped observations.
\item $R$ is the $\RegSeqRatUp$ tolerance-readback row attached to the windows and metric requests.
\item $E$ is the $\RealUp$ terminal seal read after the filter, metric, topology, window, and tolerance rows have all been displayed.
\item $A$ is the adherent-observation row. It records that every displayed neighbourhood request compatible with $T$ has a displayed filter event in $F$ whose metric tolerance is read through $M,R,E$.
\item $H$ records componentwise $\hsame$ transport for the filter, metric, topology, window, tolerance, real-seal, adherent-observation, and structural rows.
\item $C$ records displayed $\Cont$ replay from filter-base refinement to neighbourhood observation, from metric tolerance to regular rational readback, and from the adherent row to the real-seal and completion-facing handoff.
\item $P$ is the $\Pkg$ provenance over $\ClusterFilterUp$, $\CauchyFilterUp$, $\MetricSpaceUp$, $\TopologyUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ClusterFilterUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,M,T,W,R,E,A,H,C,P,N$ and the displayed routes among those rows. There is no coordinate for a host powerset of neighbourhoods, a selected cluster point, quotient equality of filters, a maximal filter, countable choice, or an ambient completion theorem.
\end{definition}
\leanchecked{BEDC.Derived.ClusterFilterUp.TasteGate.ClusterFilterTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ClusterFilter NameCert obligations]
\label{thm:cluster-filter-namecert-obligations}
For every accepted $\ClusterFilterUp$ carrier
$$
G=(F,M,T,W,R,E,A,H,C,P,N),
$$
the local $\NameCert_{\ClusterFilterUp}$ surface consists exactly of carrier admission, Cauchy-filter exposure through $F$, metric-space exposure through $M$, topology-neighbourhood exposure through $T$, finite window exposure through $W$, regular rational readback through $R$, real-seal readiness through $E$, adherent-observation exposure through $A$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cluster-filter-carrier}. The rows $F,M,T,W,R,E,A$ are the only mathematical rows available to a cluster-filter read, and $H,C,P,N$ are the only structural rows.

The filter and neighbourhood rows are read first. The row $F$ supplies finite base requests and refinements, while $T$ supplies only displayed neighbourhood observations over the metric carrier $M$.

The observation row then binds clustering to finite tolerance data. The row $A$ can cite only the displayed filter events, neighbourhood requests, stream windows, regular rational tolerances, and real seal already present in $F,M,T,W,R,E$.

Finally $H,C,P,N$ transport, replay, source, and name that same route. Since the excluded host powerset, selected cluster point, quotient filter, maximal filter, countable-choice schedule, and ambient completion theorem are absent from the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[ClusterFilter Cauchy-completion handoff]
\label{thm:cluster-filter-cauchy-completion-handoff}
Every Cauchy-completion-facing consumer of an accepted $\ClusterFilterUp$ packet must read the displayed route
$$
\CauchyFilterUp,\ \MetricSpaceUp,\ \TopologyUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp
$$
through the carrier rows $F,M,T,W,R,E$ before it may use the adherent-observation row $A$ as cluster-filter evidence. The handoff supplies a finite cluster interface for completion and compactness arguments; it supplies no selected cluster point, quotient filter, host powerset of neighbourhoods, maximal-filter principle, countable choice, ambient compactness theorem, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Start with the displayed Cauchy-filter row $F$. A completion-facing consumer can inspect only the finite filter-base requests and directed refinements carried by that row.

Next read the metric, topology, and window rows. The metric-space row $M$ supplies distance observations, the topology row $T$ supplies neighbourhood requests, and the stream row $W$ gives the finite observation windows through which those requests are probed.

The tolerance and real-seal rows are downstream. The row $R$ records the regular rational readback for each displayed request, and $E$ seals the Real-facing tolerance only after the filter, metric, topology, and window data have been displayed.

Only then can the adherent-observation row $A$ be consumed as cluster-filter evidence. The structural rows $H,C,P,N$ preserve the same finite route under transport, replay, provenance, and local naming, so no excluded choice, quotient, host-powerset, compactness, or completeness principle can enter the handoff.
\end{proof}

\falsifiablePrediction{Every accepted $\ClusterFilterUp$ completion-facing read factors through a CauchyFilter row, MetricSpace row, Topology neighbourhood row, StreamName finite-window row, RegSeqRat tolerance row, Real seal, adherent-observation row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert row.}

\independenceWitness{cauchyfilter, metric-space, topology, streamname, regseqrat, real: $\ClusterFilterUp$ is not bijective to any listed sibling because it jointly carries a visible filter row, metric-space row, topology-neighbourhood row, finite observation windows, rational tolerance readback, real seal, and adherent-observation route.}

\closureat{ClusterFilterUp}{seedStr}

\begin{closurestatus}{\ClusterFilterUp}
  \constructivestory{A $\ClusterFilterUp$ packet is generated from a CauchyFilter row, MetricSpace row, Topology neighbourhood row, StreamName finite-window row, RegSeqRat tolerance row, Real seal, adherent-observation row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cluster-filter-carrier}, \autoref{thm:cluster-filter-namecert-obligations}, and \autoref{thm:cluster-filter-cauchy-completion-handoff} seed the finite cluster-filter interface consumed by Cauchy-completion and compactness routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected cluster points, quotient filters, host powersets of neighbourhoods, maximal filters, countable choice, ambient compactness, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Cauchy-filter exposure, metric-space exposure, topology-neighbourhood exposure, finite-window exposure, tolerance readback, real-seal readiness, adherent-observation nonescape, transport, replay, provenance, and local naming for BEDC.Derived.ClusterFilterUp.}
\end{closurestatus}
