\chapter{A Concrete Naming Certificate for $\NemytskiiOperatorUp$}
\label{ch:concrete-instances-nemytskii-operator-namecert}
\origin{human}

Following Krasnoselskii and Rutickii on superposition operators, the $\NemytskiiOperatorUp$ packet records the finite NameCert surface for nonlinear pointwise composition on named function spaces. It sits over the measurable-map surface of \autoref{ch:concrete-instances-measurable-function-namecert}, the Sobolev-space carrier of \autoref{ch:concrete-instances-sobolev-space-namecert}, the complete normed-space interface of \autoref{ch:concrete-instances-banachspace-namecert}, the measure rows of \autoref{ch:concrete-instances-measure-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the displayed superposition route for a nonlinear kernel and its source-function windows; it does not assert a host function quotient, global continuity theorem, PDE solvability result, selected representative, or ambient Banach-space completeness theorem.

\begin{definition}[Nemytskii operator carrier]
\label{def:nemytskii-operator-carrier}
A $\NemytskiiOperatorUp$ carrier is a finite $\BHist$ packet
$$
T=(D,M,F,W,I,T_0,S,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the domain and codomain row, naming the measurable source, target scalar seal, and function-space boundary inspected by the packet.
\item $M$ is the $\MeasurableFunctionUp$ row for the nonlinear kernel, exposing only displayed preimage ledgers and graph-read windows.
\item $F$ is the source-function row, listing the finite function-name windows, domain probes, and scalar readbacks that may be substituted into the kernel.
\item $W$ is the pointwise witness row, pairing each displayed source observation with the corresponding displayed kernel observation before any output function row is read.
\item $I$ is the integrability and growth-budget row, binding the admissible source windows to the finite measure and Real rows used by the superposition request.
\item $T_0$ is the target-function row produced by the displayed superposition route, not by a host quotient of functions.
\item $S$ is the $\SobolevSpaceUp$ or function-space handoff row, available only after $D,M,F,W,I,T_0$ have been displayed.
\item $R$ is the $\RealUp$ readback row for scalar kernel values, growth budgets, norm estimates, and target-function observations.
\item $H$ stores componentwise $\hsame$ transport for domain, measurable-kernel, source-function, witness, integrability, target-function, function-space, Real, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from every superposition request through $D,M,F,W,I,T_0,S,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\NemytskiiOperatorUp$, $\MeasurableFunctionUp$, $\SobolevSpaceUp$, $\BanachSpaceUp$, $\MeasureUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\NemytskiiOperatorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for an ambient nonlinear operator theorem, quotient equality of functions, almost-everywhere representative choice, global compactness, PDE solvability, or an external Banach-space completeness claim.
\end{definition}
\leanstmt{BEDC.Derived.NemytskiiOperatorUp}

\begin{theorem}[Nemytskii operator NameCert obligations]
\label{thm:nemytskii-operator-namecert-obligations}
For every accepted $\NemytskiiOperatorUp$ carrier
$$
T=(D,M,F,W,I,T_0,S,R,H,C,P,N),
$$
the local $\NameCert_{\NemytskiiOperatorUp}$ surface consists exactly of carrier admission for the domain row $D$, measurable-kernel row $M$, source-function row $F$, pointwise witness row $W$, integrability and growth row $I$, target-function row $T_0$, function-space handoff $S$, Real readback $R$, componentwise transport $H$, displayed replay $C$, provenance $P$, and local naming $N$. Every admitted nonlinear composition read must expose the kernel row, source windows, pointwise witness row, growth budget, target-function row, and Real seal before a Sobolev, Banach, measure, or Real consumer can read the output.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:nemytskii-operator-carrier}. The only analytic data available to the classifier are the displayed domain row $D$, measurable-kernel row $M$, source-function row $F$, pointwise witness row $W$, integrability row $I$, target row $T_0$, function-space handoff $S$, and Real row $R$.

The measurable-kernel obligation is read before any output claim. The preimage and graph-read surface of $M$ fixes which nonlinear kernel observations can be paired with the source-function windows in $F$.

The pointwise witness and budget rows then bind the superposition route. The rows $W,I,T_0,R$ record the displayed source-to-target observation pairs, growth and integrability budgets, target-function output, and scalar readbacks.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since the excluded host objects are not coordinates of the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Nemytskii operator measurable handoff]
\label{thm:nemytskii-operator-measurable-handoff}
Every measurable-output read exported by an accepted $\NemytskiiOperatorUp$ carrier factors through the finite route
$$
M,F,W,I \longmapsto T_0 \longmapsto R \longmapsto H,C,P,N.
$$
The route exposes a measurable-kernel ledger, source-function windows, displayed pointwise substitutions, growth and integrability budgets, target-function rows, Real readbacks, transport, replay, provenance, and local naming. It does not export a host inverse-image function, almost-everywhere quotient, selected representative, global continuity theorem, or completed measure space.
\end{theorem}
\begin{proof}
Start with a measurable-output request. The request first reads the measurable-kernel row $M$ and the source-function row $F$, because the output is determined only by the displayed kernel observations paired with displayed source observations.

Next the route inspects $W$ and $I$. These rows bind pointwise substitution and admissible growth or integrability budgets to the same finite windows, and the target-function row $T_0$ is read only after those rows are fixed.

The Real readback and structural rows close the route. The scalar seal $R$ and the rows $H,C,P,N$ preserve the same packet, so no host inverse-image function, representative selector, quotient, continuity theorem, or measure completion is exported.
\end{proof}

\begin{theorem}[Nemytskii operator Banach--Sobolev consumer]
\label{thm:nemytskii-operator-banach-sobolev-consumer}
Every Banach--Sobolev consumer of an accepted $\NemytskiiOperatorUp$ carrier must read the displayed route
$$
\MeasurableFunctionUp,\ \MeasureUp,\ \RealUp,\ \SobolevSpaceUp,\ \BanachSpaceUp
$$
through the carrier rows $M,I,R,S$ and the source-to-target rows $F,W,T_0$ before it may consume transport, replay, provenance, or local naming. The handoff supplies a finite nonlinear composition interface; it does not assert a compact embedding, a global boundedness theorem, PDE solvability, quotient equality of functions, countable choice, or an ambient completeness theorem.
\end{theorem}
\begin{proof}
Use the NameCert obligations of \autoref{thm:nemytskii-operator-namecert-obligations}. They force every consumer to begin with the measurable kernel and source-function rows, then pass through the pointwise witness and growth-budget rows.

The Sobolev and Banach reads are downstream of $S$ and of the Real readback row $R$. Thus any function-space statement consumes only the displayed target-function row $T_0$, the finite budget row $I$, and the sibling certificates named in the provenance row.

Transport, replay, provenance, and local naming through $H,C,P,N$ keep the same finite route. Since no compact embedding, selected representative, quotient equality, choice schedule, PDE theorem, or ambient completeness coordinate appears in the carrier, every Banach--Sobolev consumer is exhausted by the displayed handoff.
\end{proof}

\falsifiablePrediction{An accepted $\NemytskiiOperatorUp$ consumer that reaches a Sobolev or Banach read without first exposing measurable-kernel rows, source-function windows, pointwise witness rows, growth budgets, target-function rows, Real readbacks, componentwise hsame transport, Cont replay, Pkg provenance, and local naming refutes the carrier surface of \autoref{def:nemytskii-operator-carrier}.}

\independenceWitness{measurable-function, sobolev-space, banach-space, measure, real: no listed sibling supplies the whole twelve-row packet $T=(D,M,F,W,I,T_0,S,R,H,C,P,N)$, because each sibling contributes only kernel measurability, function-space, normed-completion, measure, or scalar-seal data while this chapter binds them into one nonlinear superposition carrier.}

\closureat{NemytskiiOperatorUp}{seedStr}

\begin{closurestatus}{\NemytskiiOperatorUp}
  \constructivestory{A $\NemytskiiOperatorUp$ packet is generated from a displayed domain row, MeasurableFunction kernel row, source-function windows, pointwise witness rows, growth and integrability budgets, target-function rows, Sobolev or function-space handoff data, Real readbacks, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:nemytskii-operator-carrier}, \autoref{thm:nemytskii-operator-namecert-obligations}, \autoref{thm:nemytskii-operator-measurable-handoff}, and \autoref{thm:nemytskii-operator-banach-sobolev-consumer} seed the finite nonlinear superposition surface over displayed measurable kernels, source windows, pointwise witnesses, growth budgets, target rows, function-space handoffs, Real readbacks, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global continuity, compact embedding, PDE solvability, almost-everywhere quotient equality, selected representatives, countable choice, ambient Banach-space completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, measurable-kernel handoff, pointwise witness exactness, growth-budget routing, Banach--Sobolev consumer nonescape, transport, replay, provenance, and local naming for BEDC.Derived.NemytskiiOperatorUp.}
\end{closurestatus}
