\chapter{A Concrete Naming Certificate for $\CompactUniformRadiusTransportUp$}
\label{ch:concrete-instances-compact-uniform-radius-transport-namecert}
\origin{human}

Following Bishop and Bridges and the constructive Heine--Cantor route, the $\CompactUniformRadiusTransportUp$ packet packages the finite radius-transport step used by \autoref{ch:visions-compact-uniform-continuity}. It sits beside the compact source packet of \autoref{ch:concrete-instances-compact-namecert}, the metric distance surface of \autoref{ch:concrete-instances-metric-namecert}, the continuous-map carrier of \autoref{ch:concrete-instances-continuousmap-namecert}, the rational radius ledger of \autoref{ch:concrete-instances-rat-namecert}, and the uniform-modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet names a finite transport from pointwise compact-cover radii to a tolerance-only modulus ledger; it does not choose a global modulus by countable choice or by an ambient compactness principle.

\begin{definition}[Compact uniform radius transport carrier]
\label{def:compact-uniform-radius-transport-carrier}
A $\CompactUniformRadiusTransportUp$ carrier is a finite $\BHist$ packet
$$
T=(K,M,F,R,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactUp$ finite-net row, including the bundled compact-cover witnesses used at the requested tolerance.
\item $M$ is the $\MetricSpaceUp$ distance row for the source and target metric comparisons consumed by the transport.
\item $F$ is the $\ContinuousMapUp$ pointwise-modulus row attached to the compact finite-net centers.
\item $R$ is the $\RatUp$ positive-radius and lower-bound fold ledger for the finitely many displayed radii.
\item $U$ is the $\UniformModulusUp$ handoff row reached only after $K,M,F,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $K,M,F,R,U,C,P,N$.
\item $C$ records displayed $\Cont$ replay from compact finite-net coverage through pointwise radii, rational lower-bound folding, metric triangle use, and the uniform-modulus handoff.
\item $P$ is the $\Pkg$ provenance over $\CompactUniformRadiusTransportUp$, $\CompactUp$, $\MetricSpaceUp$, $\ContinuousMapUp$, $\RatUp$, $\UniformModulusUp$, $\BHist$, $\hsame$, $\Cont$, and the local naming row.
\item $N$ is the local $\NameCert_{\CompactUniformRadiusTransportUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $K,M,F,R,U,H,C,P,N$. It has no coordinate for an external modulus selector, an infinite cover, countable choice, open-cover compactness outside the displayed finite net, host real equality, or ambient Real completeness.
\end{definition}

\begin{theorem}[Compact uniform radius transport NameCert obligations]
\label{thm:compact-uniform-radius-transport-namecert-obligations}
For every accepted $\CompactUniformRadiusTransportUp$ carrier
$$
T=(K,M,F,R,U,H,C,P,N),
$$
the local $\NameCert_{\CompactUniformRadiusTransportUp}$ surface consists exactly of compact finite-net admission, metric-distance compatibility, continuous-map pointwise-radius admission, rational lower-bound fold compatibility, uniform-modulus handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. The certificate cannot export an external modulus selector, infinite cover, countable choice, open-cover compactness detached from $K$, host real equality, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-uniform-radius-transport-carrier}. The compact-cover and analytic rows are $K,M,F,R,U$, while $H,C,P,N$ are the structural rows that preserve the same displayed transport.

The compact finite-net row $K$ exposes only finitely many centers and coverage witnesses. The continuous-map row $F$ supplies pointwise radii at those displayed centers, and the rational ledger $R$ folds the finitely many positive radii before the uniform-modulus row $U$ is available.

Metric compatibility is read through $M$ along the same route. Since no carrier coordinate names an external selector, infinite cover, countable-choice schedule, detached open-cover compactness theorem, host real equality, or ambient completeness principle, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Compact uniform radius transport handoff]
\label{thm:compact-uniform-radius-transport-handoff}
Every uniform-modulus consumer of an accepted $\CompactUniformRadiusTransportUp$ packet receives the finite route
$$
K,M,F,R,U,H,C,P,N .
$$
The handoff transports pointwise compact-cover radii through the displayed compact finite net, source and target metric rows, continuous-map local-modulus data, and $\RatUp$ lower-bound folding before exposing the $\UniformModulusUp$ row. It may be used as the radius-transport step in compact-uniform-continuity arguments, but it cannot be reinterpreted as an external modulus selector, an infinite cover, countable choice, detached open-cover compactness, host real equality, or ambient Real completeness.
\end{theorem}
\begin{proof}
Apply the NameCert obligation theorem. It forces the compact finite-net row $K$ before any pointwise radius can be consumed, and it forces the continuous-map row $F$ and rational lower-bound row $R$ before the uniform-modulus handoff $U$ is exposed.

The compact-uniform-continuity vision of \autoref{ch:visions-compact-uniform-continuity} uses exactly this order: finite compact-cover data first, pointwise local radii second, rational lower-bound folding third, and the tolerance-only uniform-modulus row last. Metric rows in $M$ supply the triangle comparisons without adding a host compactness theorem.

Finally replay $H,C,P,N$. These rows preserve the displayed finite transport and do not create any coordinate for external selection, infinite covers, countable choice, detached open-cover compactness, host equality, or ambient completeness.
\end{proof}

\begin{closurestatus}{\CompactUniformRadiusTransportUp}
  \constructivestory{A $\CompactUniformRadiusTransportUp$ packet is generated from Compact finite-net rows, MetricSpace distance rows, ContinuousMap pointwise-radius rows, Rat lower-bound folds, a UniformModulus handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-radius-transport-carrier}, \autoref{thm:compact-uniform-radius-transport-namecert-obligations}, and \autoref{thm:compact-uniform-radius-transport-handoff} seed the finite radius-transport surface from compact pointwise radii to UniformModulus consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close external modulus selection, infinite covers, countable choice, open-cover compactness outside the displayed finite net, host real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net routing, metric compatibility, continuous-map pointwise-radius admission, rational lower-bound folding, uniform-modulus handoff, transport, replay, provenance, and local naming for BEDC.Derived.CompactUniformRadiusTransportUp.}
\end{closurestatus}
