\chapter{A Concrete Naming Certificate for $\ObserverPhaseGroupoidUp$}
\label{ch:concrete-instances-observer-phase-groupoid-namecert}
\origin{ai}

The $\ObserverPhaseGroupoidUp$ packet realizes the reversible phase-surface transport direction of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite object, arrow, inverse, composition, boundary-refusal, provenance, and local naming rows. It consumes the visible phase surface of \autoref{ch:concrete-instances-complex-namecert}, reversible transport through \autoref{ch:concrete-instances-unitarygroup-namecert}, finite flow-style replay through \autoref{ch:concrete-instances-dynsystem-namecert}, the observer-expansion route of \autoref{ch:concrete-instances-hyperbolic-observer-expansion-namecert}, and the boundary-far-end refusal of \autoref{ch:concrete-instances-boundary-far-end-noncenter-namecert}. The packet is a finite transport groupoid surface, not a host groupoid of all observers and not a completed phase space.

\begin{definition}[Observer phase groupoid carrier]
\label{def:observer-phase-groupoid-carrier}
An $\ObserverPhaseGroupoidUp$ carrier is a finite $\BHist$ packet
$$
G=(O,A,S,T,I,M,B,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the finite object row of observer-side phase surfaces.
\item $A$ is the finite arrow row of reversible phase transports between displayed objects.
\item $S$ is the source-target incidence row tying each arrow to two displayed phase objects.
\item $T$ is the reversible transport row, read through the $\UnitaryGroupUp$ and $\DynSystemUp$ surfaces.
\item $I$ is the inverse row, giving the displayed reverse transport for every accepted arrow.
\item $M$ is the composition row, giving the displayed composite when source and target rows match.
\item $B$ is the boundary-refusal row, excluding an interior center, a global observer object, and a boundary far-end treated as a phase object.
\item $H$ records componentwise $\hsame$ transport for object, arrow, incidence, transport, inverse, composition, and boundary-refusal rows.
\item $C$ records displayed $\Cont$ replay through phase objects, reversible transport, inverse, composition, and refusal reads.
\item $P$ is the $\Pkg$ provenance over $\ComplexUp$, $\UnitaryGroupUp$, $\DynSystemUp$, $\HyperbolicObserverExpansionUp$, $\BoundaryFarEndNoncenterUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ObserverPhaseGroupoidUp}$ row.
\end{enumerate}
The classifier compares arrows only by the joint object-arrow-incidence, inverse, composition, refusal, transport, replay, provenance, and local naming surface. It contains no host phase groupoid, quotient observer identity, global time, or completed hyperbolic phase space.
\end{definition}

\begin{theorem}[Observer phase groupoid NameCert obligations]
\label{thm:observer-phase-groupoid-namecert-obligations}
For every accepted $\ObserverPhaseGroupoidUp$ carrier $G=(O,A,S,T,I,M,B,H,C,P,N)$, the local $\NameCert_{\ObserverPhaseGroupoidUp}$ surface consists exactly of object admission, arrow admission, source-target incidence, reversible transport, inverse, composition, boundary refusal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every accepted arrow factors through displayed phase object rows, reversible transport, inverse, composition, boundary refusal, hsame, Cont, Pkg, and NameCert rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:observer-phase-groupoid-carrier}. The object and arrow rows are $O$ and $A$, while $S$ records the finite source-target incidence that makes an arrow readable.

The transport, inverse, and composition rows are displayed separately as $T,I,M$. They are therefore part of the same finite surface rather than hidden operations on a host groupoid.

Boundary refusal is row $B$. It prevents the far-end boundary and observer-side focus from becoming ordinary phase objects, so accepted arrows remain reversible display transports rather than global observer identities.

Finally, $H,C,P,N$ transport, replay, source, and name the same rows. No further row remains, so the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Observer phase groupoid transport composition]
\label{thm:observer-phase-groupoid-transport-composition}
Whenever two accepted $\ObserverPhaseGroupoidUp$ arrows have matching displayed incidence rows, their composite is the row supplied by $M$ after reading the same object surface $O$, arrow surface $A$, reversible transport row $T$, inverse row $I$, boundary-refusal row $B$, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The composite exports no host observer equality, quotient phase object, global clock, or completed hyperbolic geometry.
\end{theorem}
\begin{proof}
Read the two arrows through $A$ and their source-target incidence through $S$. The matching condition is therefore a displayed row comparison, not a host equality of observers.

Use the reversible transport and inverse rows $T,I$ to keep each arrow inside the accepted phase-transport surface. The composition row $M$ is then the only row allowed to expose the composite.

Transport through $H$ and replay through $C$ preserve the same object, arrow, inverse, composition, and refusal rows. Provenance and local naming through $P,N$ certify that the composite remains in the finite packet.

Since no quotient phase object, host observer equality, global clock, or completed hyperbolic geometry is present in the carrier, composition remains a finite BEDC row.
\end{proof}

\falsifiablePrediction{Every accepted $\ObserverPhaseGroupoidUp$ arrow factors through displayed phase object rows, reversible transport, inverse, composition, boundary refusal, hsame, Cont, Pkg, and NameCert rows.}

\independenceWitness{complex, unitarygroup, dynsystem, hyperbolic-observer-expansion, boundary-far-end-noncenter: none is bijective to $\ObserverPhaseGroupoidUp$ because the groupoid packet jointly carries object rows, arrow rows, incidence, reversible transport, inverse, composition, boundary refusal, hsame transport, Cont replay, provenance, and local naming.}

The Lean follow-up for this packet provides explicit $\mathsf{Nontrivial}\ \ObserverPhaseGroupoidUp$ and $\mathsf{FieldFaithful}\ \ObserverPhaseGroupoidUp$ TasteGate instances in $\mathsf{BEDC.Derived.ObserverPhaseGroupoidUp.TasteGate}$. The paper-side chapter remains a finite NameCert target; bridge checking is a separate closure axis.

\closureat{ObserverPhaseGroupoidUp}{seedStr}

\begin{closurestatus}{\ObserverPhaseGroupoidUp}
  \constructivestory{An $\ObserverPhaseGroupoidUp$ packet is generated from finite phase-object rows, arrow rows, source-target incidence, reversible transport, inverse, composition, boundary refusal, hsame transport, Cont replay, Pkg provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:observer-phase-groupoid-carrier}, \autoref{thm:observer-phase-groupoid-namecert-obligations}, and \autoref{thm:observer-phase-groupoid-transport-composition} seed the finite reversible phase groupoid route over objects, arrows, incidence, inverse, composition, boundary refusal, transport, replay, provenance, and naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a host observer groupoid, quotient phase object, global clock, completed hyperbolic phase space, Lean verification of the paper obligations, or bridge checking for $\ObserverPhaseGroupoidUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, object-arrow incidence, reversible transport, inverse, composition, boundary refusal, TasteGate nontriviality, field faithfulness, and local naming for BEDC.Derived.ObserverPhaseGroupoidUp.}
\end{closurestatus}
