\chapter{A Concrete Naming Certificate for $\UniformSpaceRealCompletionUp$}
\label{ch:concrete-instances-uniform-space-real-completion-namecert}
\origin{human}

Following Bourbaki, Kelley, and Bishop--Bridges, the $\UniformSpaceRealCompletionUp$ packet records the finite route by which the real uniform structure and Cauchy-filter completion data become visible to Real and Completion consumers. It sits after the real-uniformity surface of \autoref{ch:concrete-instances-real-uniform-structure-namecert}, the entourage interface of \autoref{ch:concrete-instances-uniformspace-namecert}, the complete-uniform-space boundary of \autoref{ch:concrete-instances-complete-uniform-space-namecert}, the Cauchy-filter packet of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the finite stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a displayed completion interface; it is not a quotient of streams, a selected limit operator, a trichotomy principle, countable choice, or an ambient completeness theorem beyond the rows it carries.

\begin{definition}[Uniform-space real-completion carrier]
\label{def:uniform-space-real-completion-carrier}
A $\UniformSpaceRealCompletionUp$ carrier is a finite $\BHist$ packet
$$
U=(R,U,F,B,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ is the $\RealUniformStructureUp$ row exposing the real-name source together with the displayed uniform structure induced on real observations.
\item $U$ is the $\UniformSpaceUp$ entourage row for that same real-uniform source, carrying only the finite entourage comparisons visible to a completion request.
\item $F$ is the $\CauchyFilterUp$ row naming the Cauchy-filter request that the completion consumer may inspect.
\item $B$ is a Cauchy-filter basis or completion-basis row refining $F$ to the finite family of filter and entourage requests used by the packet.
\item $S$ is the $\StreamNameUp$ finite-window row through which real-name observations are scheduled.
\item $Q$ is the $\RegSeqRatUp$ readback row converting the scheduled stream windows into regular rational approximation data.
\item $E$ is the $\RealUp$ seal reached only after the real-uniform source, entourage row, Cauchy-filter row, finite basis, StreamName window, and RegSeqRat readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for the real-uniform source, entourage row, Cauchy-filter row, basis row, stream windows, rational readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a real-completion request through $R,U,F,B,S,Q,E,H$.
\item $P$ is the $\Pkg$ provenance over $\UniformSpaceRealCompletionUp$, $\RealUniformStructureUp$, $\UniformSpaceUp$, $\CompleteUniformSpaceUp$, $\CauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformSpaceRealCompletionUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these eleven rows. It has no coordinate for quotient stream equality, a selected representative of a completion, countable choice, real trichotomy, or a host-level completeness theorem.
\end{definition}

\begin{theorem}[Uniform-space real-completion NameCert obligations]
\label{thm:uniform-space-real-completion-namecert-obligations}
For every accepted $\UniformSpaceRealCompletionUp$ carrier $T=(R,U,F,B,S,Q,E,H,C,P,N)$, the local $\NameCert_{\UniformSpaceRealCompletionUp}$ surface consists exactly of carrier admission, Real uniform-structure admission, entourage-row admission, Cauchy-filter admission, finite basis admission, StreamName finite-window admission, RegSeqRat readback, Real seal admission, componentwise transport, replay, provenance, and local naming for the displayed rows $R,U,F,B,S,Q,E,H,C,P,N$.
\end{theorem}
\begin{proof}
Project the accepted packet. Carrier admission reads the real-uniform source $R$, the entourage row $U$, the Cauchy-filter row $F$, the finite basis row $B$, the stream-window row $S$, the rational readback $Q$, and the Real seal $E$.

The completion-facing rows are ordered. A request first sees the real-induced uniformity and entourage data, then the Cauchy-filter and basis rows, and only then the finite StreamName and RegSeqRat readback that can be sealed as Real data.

Transport and replay do not widen the route. The row $H$ transports the displayed components, $C$ replays the same route, $P$ records the sibling provenance, and $N$ names the local certificate.

Since no row stores quotient stream equality, a selected completion representative, countable choice, trichotomy, or host completeness, no local NameCert consumer can recover those principles from the packet.
\end{proof}

\begin{theorem}[Uniform-space real-completion Cauchy handoff]
\label{thm:uniform-space-real-completion-cauchy-handoff}
Every Real or Completion consumer of an accepted $\UniformSpaceRealCompletionUp$ carrier receives Cauchy completion data only through the displayed route
$$
\RealUniformStructureUp,\ \UniformSpaceUp,\ \CauchyFilterUp
\longmapsto
\StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
The handoff supplies a finite real-uniform source, entourage comparisons, a Cauchy-filter request, a finite basis, scheduled stream windows, regular rational readback, and a Real seal, all transported and replayed through $H,C,P,N$. It supplies no quotient stream, selected limit, endpoint trichotomy, countable choice, or ambient completeness theorem.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:uniform-space-real-completion-carrier}. The only completion-facing source rows are the real-uniform row $R$, the entourage row $U$, the Cauchy-filter row $F$, and the basis row $B$.

The finite observation route is downstream of those rows. StreamName windows $S$ schedule the visible requests, RegSeqRat readback $Q$ exposes rational approximation data, and the Real seal $E$ is read only after those finite rows are displayed.

Finally apply the NameCert obligations of \autoref{thm:uniform-space-real-completion-namecert-obligations}. They force transport, replay, provenance, and local naming through $H,C,P,N$, and the carrier has no coordinate from which a quotient stream, selected limit, trichotomy, choice principle, or independent completeness theorem could be exported.
\end{proof}

\closureat{$\UniformSpaceRealCompletionUp$}{seedStr}

\begin{closurestatus}{\UniformSpaceRealCompletionUp}
  \constructivestory{A $\UniformSpaceRealCompletionUp$ packet is generated from a RealUniformStructure row, a UniformSpace entourage row, a CauchyFilter row, a finite completion-basis row, StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-space-real-completion-carrier}, \autoref{thm:uniform-space-real-completion-namecert-obligations}, and \autoref{thm:uniform-space-real-completion-cauchy-handoff} seed the finite real-uniform completion route over Real uniformity, entourage, Cauchy-filter, StreamName, RegSeqRat, and Real seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient streams, selected completion representatives, trichotomy, countable choice, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, entourage admission, Cauchy-filter basis exactness, finite stream-window readback, Real seal non-escape, transport, replay, provenance, and local naming for BEDC.Derived.UniformSpaceRealCompletionUp.}
\end{closurestatus}
