\chapter{A Concrete Naming Certificate for $\RegularCauchySubnetSelectorUp$}
\label{ch:concrete-instances-regular-cauchy-subnet-selector-namecert}
\origin{human}

Following Bishop-style cofinal selection in constructive Cauchy arguments, the $\RegularCauchySubnetSelectorUp$ packet records the finite route by which a regular Cauchy family supplies a cofinal subnet or subsequence window for diagonal-limit consumers. It sits over the finite observation discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the tail-equivalence boundary of \autoref{ch:concrete-instances-cauchy-tail-equivalence-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite selector certificate for cofinal Cauchy windows, not countable choice, a quotient stream, a selected real limit, or ambient completeness of $\RealUp$.

\begin{definition}[Regular Cauchy subnet selector carrier]
\label{def:regular-cauchy-subnet-selector-carrier}
A $\RegularCauchySubnetSelectorUp$ carrier is a finite $\BHist$ packet
$$
S=(X,I,W,R,D,E,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the source regular Cauchy family row whose visible windows are being routed to a cofinal selector.
\item $I$ is the cofinal index ledger. It records the finite monotone or directed comparison data needed to show that each requested tail window is eventually reached.
\item $W$ is the $\StreamNameUp$ finite-window row for the source family and selected subnet windows.
\item $R$ is the $\RegSeqRatUp$ readback row extracted from the displayed selected windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row carrying the dyadic budgets used by $I,W,R$.
\item $E$ is the terminal $\RealUp$ seal reached only after the selected windows and tolerance row have been displayed.
\item $T$ is the $\CauchyTailEquivalenceUp$ witness row recording that the selected cofinal windows preserve the same regular Cauchy tail route as the source family.
\item $H$ records componentwise $\hsame$ transport for $X,I,W,R,D,E,T$.
\item $C$ records displayed $\Cont$ replay of source-family admission, cofinal-index inspection, stream-window extraction, regular rational readback, dyadic tolerance comparison, real-seal handoff, and tail-equivalence transport.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchySubnetSelectorUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\CauchyTailEquivalenceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\RegularCauchySubnetSelectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,I,W,R,D,E,T,H,C,P,N$ and exports no countable-choice selector, quotient stream equality, selected limit, host subnet object, trichotomy, or ambient $\RealUp$ completeness coordinate.
\end{definition}

\begin{theorem}[Regular Cauchy subnet selector NameCert obligations]
\label{thm:regular-cauchy-subnet-selector-namecert-obligations}
For every accepted $\RegularCauchySubnetSelectorUp$ carrier
$$
S=(X,I,W,R,D,E,T,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchySubnetSelectorUp}$ surface consists exactly of carrier admission for the source regular Cauchy family, cofinal index ledger, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance row, $\RealUp$ seal, $\CauchyTailEquivalenceUp$ witness, componentwise transport, displayed replay, package provenance, and local naming rows. Every accepted selector read must expose $I$ before it consumes $W$, expose $W,D$ before it consumes $R$, expose $R,D,T$ before it consumes $E$, and reach $H,C,P,N$ only as structural support for that same finite route.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-subnet-selector-carrier}. The mathematical rows are exactly the source family $X$, the cofinal ledger $I$, the window row $W$, the readback row $R$, the tolerance row $D$, the real seal $E$, and the tail-equivalence row $T$.

The cofinal ledger is inspected before any selected window is read. This prevents the selector from acting as a free choice principle; each visible subnet window is justified by the finite comparison data already stored in $I$.

The regular Cauchy data then flows through $W,R,D,T$ before reaching the real seal $E$. Transport through $H$, replay through $C$, provenance through $P$, and local naming through $N$ preserve that route and add no quotient stream, selected limit, host subnet object, trichotomy, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Regular Cauchy subnet selector handoff]
\label{thm:regular-cauchy-subnet-selector-handoff}
Every diagonal-limit or real-completeness read from an accepted $\RegularCauchySubnetSelectorUp$ carrier factors through
$$
\StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp,\ \CauchyTailEquivalenceUp
$$
before the selected cofinal windows may be consumed. The exported route contains only the source regular Cauchy family row, cofinal index ledger, finite stream windows, regular rational readback, dyadic tolerance row, real seal, tail-equivalence witness, transport, replay, provenance, and local naming; it exports no countable choice, quotient stream equality, selected real limit, host subnet object, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the obligation package of \autoref{thm:regular-cauchy-subnet-selector-namecert-obligations}. A consumer cannot inspect selected windows until the cofinal index ledger $I$ has displayed the finite directed comparison route for the requested tail.

Next route the selected windows through the regular Cauchy surface. The stream row $W$, regular rational readback $R$, dyadic tolerance row $D$, and tail-equivalence witness $T$ jointly account for the finite-window extraction before the terminal $\RealUp$ seal $E$ can be used.

The structural rows $H,C,P,N$ transport, replay, source, and name the same handoff. Since the carrier has no coordinate for countable choice, quotient stream equality, selected limits, host subnet objects, trichotomy, or ambient completeness, the displayed route is the entire consumer surface.
\end{proof}

\falsifiablePrediction{Every accepted $\RegularCauchySubnetSelectorUp$ diagonal-limit read displays a source regular Cauchy family row, a cofinal index ledger, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance data, a CauchyTailEquivalence witness, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming before real-completeness consumers can inspect it.}

\independenceWitness{streamname, regseqrat, dyadicratcore, cauchy-tail-equivalence, real: $\RegularCauchySubnetSelectorUp$ is not bijective to any listed sibling because it binds cofinal index data to selected regular Cauchy windows and their tail-equivalence route as one finite selector packet.}

\closureat{RegularCauchySubnetSelectorUp}{seedStr}

\begin{closurestatus}{\RegularCauchySubnetSelectorUp}
  \constructivestory{A $\RegularCauchySubnetSelectorUp$ packet is generated from a source regular Cauchy family, a cofinal index ledger, StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance row, a RealUp seal, a CauchyTailEquivalence witness, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-subnet-selector-carrier}, \autoref{thm:regular-cauchy-subnet-selector-namecert-obligations}, and \autoref{thm:regular-cauchy-subnet-selector-handoff} seed the finite cofinal-window selector surface for diagonal-limit and real-completeness consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, quotient stream equality, selected real limits, host subnet objects, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, cofinal-ledger exposure, finite-window extraction, regular readback, dyadic tolerance accounting, Real seal handoff, tail-equivalence preservation, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchySubnetSelectorUp.}
\end{closurestatus}
