\chapter{A Concrete Naming Certificate for $\TotalBoundednessModulusUp$}
\label{ch:concrete-instances-total-boundedness-modulus-namecert}
\origin{human}

Following Bishop and Bridges on constructive metric compactness, the $\TotalBoundednessModulusUp$ packet records the finite-net schedule by which a totally bounded metric source supplies explicit net rows at each displayed tolerance. It sits after the $\MetricSpaceUp$ metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the total-boundedness certificate of \autoref{ch:concrete-instances-totallybounded-namecert}, the compact metric surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite modulus neighbour for the L10 compact-metric route; it is not an open-cover compactness theorem, a selected subcover, a quotient point equality principle, or an ambient completeness assertion.

\begin{definition}[Total boundedness modulus carrier]
\label{def:total-boundedness-modulus-carrier}
A $\TotalBoundednessModulusUp$ carrier is a finite $\BHist$ packet
$$
T=(M,N,D,R,E,H,C,P,L)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\MetricSpaceUp$ source row, carrying point classifiers, distance observations, and metric comparison data.
\item $N$ is the $\TotallyBoundedUp$ finite-net schedule row, assigning each admitted positive tolerance a finite displayed center list and coverage witness.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording halving, comparison, and positivity reads used by the net schedule.
\item $R$ is the $\RealUp$ seal row through which metric distances and tolerance comparisons are exposed to compact-metric consumers.
\item $E$ is the $\CompactMetricUp$ handoff row, recording that compact-metric consumers may read the modulus only after the metric, total-boundedness, dyadic, and real-seal rows are visible.
\item $H$ records componentwise $\hsame$ transport for the metric, finite-net schedule, dyadic tolerance, real seal, compact handoff, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact-metric request through $M,N,D,R,E,H,P,L$.
\item $P$ is the $\Pkg$ provenance over $\TotalBoundednessModulusUp$, $\MetricSpaceUp$, $\TotallyBoundedUp$, $\CompactMetricUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $L$ is the local $\NameCert_{\TotalBoundednessModulusUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $M,N,D,R,E,H,C,P,L$. It has no coordinate for arbitrary open covers, selected finite subcovers, countable choice, quotient point equality, host metric completeness, or an ambient $\RealUp$ equality relation.
\end{definition}

\begin{theorem}[Total boundedness modulus NameCert obligations]
\label{thm:total-boundedness-modulus-namecert-obligations}
For every accepted $\TotalBoundednessModulusUp$ carrier $T=(M,N,D,R,E,H,C,P,L)$, the local $\NameCert_{\TotalBoundednessModulusUp}$ surface consists exactly of carrier admission for $T$, metric-source admission through $M$, finite-net schedule exposure through $N$, dyadic tolerance accounting through $D$, real-seal exposure through $R$, compact-metric handoff through $E$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $L$.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:total-boundedness-modulus-carrier}. The metric source is $M$, the schedule row is $N$, and the tolerance arithmetic is $D$.

The real-facing and compact-facing rows are $R$ and $E$. They expose distance and tolerance comparisons only after the metric and finite-net schedule rows are visible, so a consumer cannot replace the packet by an open-cover compactness principle or by a selected subcover.

Finally the structural rows $H,C,P,L$ transport, replay, source, and name the same finite route. Since no additional coordinate is present, the listed rows exhaust the NameCert obligations and no quotient point equality, countable-choice schedule, host completeness, or ambient $\RealUp$ equality can be exported.
\end{proof}

\begin{theorem}[Total boundedness modulus finite-net handoff]
\label{thm:total-boundedness-modulus-finite-net-handoff}
Every $\CompactMetricUp$, $\ContinuousMapUp$, or completion-facing consumer of an accepted $\TotalBoundednessModulusUp$ carrier receives finite-net data only through the displayed route
$$
\MetricSpaceUp,\ \TotallyBoundedUp,\ \DyadicRatCoreUp,\ \RealUp
\longmapsto
\CompactMetricUp .
$$
For each admitted positive dyadic tolerance, the consumer may inspect the finite center list and coverage row carried by $N$, the tolerance comparison ledger $D$, the real-valued distance seal $R$, and the compact-metric handoff $E$, together with $H,C,P,L$. It receives no open-cover compactness theorem, selected finite subcover, countable-choice schedule, quotient point equality, host metric completeness, or ambient $\RealUp$ equality.
\end{theorem}
\begin{proof}
Start from \autoref{def:total-boundedness-modulus-carrier}. The source metric row $M$ and the total-boundedness row $N$ are the only rows that can expose centers and coverage witnesses.

Read the tolerance and distance boundary through $D$ and $R$. The dyadic ledger controls each positive request, and the real seal exposes the corresponding distance comparison before the compact-metric handoff is available.

Apply the obligation surface of \autoref{thm:total-boundedness-modulus-namecert-obligations}. It forces the compact-facing row $E$ and the structural rows $H,C,P,L$ to remain visible for every handoff.

Because the carrier contains no open-cover, subcover-selection, choice, quotient, host-completeness, or ambient-real-equality coordinate, the finite-net handoff cannot export any of those objects.
\end{proof}

\falsifiablePrediction{Every accepted $\TotalBoundednessModulusUp$ finite-net read factors through one $\MetricSpaceUp$ source row, one $\TotallyBoundedUp$ schedule row, one $\DyadicRatCoreUp$ tolerance ledger, one $\RealUp$ distance seal, one $\CompactMetricUp$ handoff row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming.}

\independenceWitness{metric, totallybounded, compactmetric, dyadicratcore, real: $\TotalBoundednessModulusUp$ is not bijective to any listed sibling because it jointly binds metric observations, tolerance-indexed finite-net schedules, dyadic tolerance arithmetic, Real-facing distance seals, compact-metric handoff, transport, replay, provenance, and local naming.}

\closureat{TotalBoundednessModulusUp}{seedStr}

\begin{closurestatus}{\TotalBoundednessModulusUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:total-boundedness-modulus-carrier}, \autoref{thm:total-boundedness-modulus-namecert-obligations}, and \autoref{thm:total-boundedness-modulus-finite-net-handoff} seed the finite-net modulus route over MetricSpace, TotallyBounded, CompactMetric, DyadicRatCore, and Real rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected finite subcovers, countable choice, quotient point equality, host metric completeness, ambient Real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, metric-source admission, finite-net schedule exposure, dyadic tolerance exactness, Real seal handoff, compact-metric handoff, structural transport, replay, provenance, and local naming for BEDC.Derived.TotalBoundednessModulusUp.}
  \constructivestory{A $\TotalBoundednessModulusUp$ packet is generated from a MetricSpaceUp source row, a TotallyBoundedUp finite-net schedule, a DyadicRatCoreUp tolerance ledger, a RealUp distance seal, a CompactMetricUp handoff row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
