\chapter{A Concrete Naming Certificate for $\KleeneTreeBoundaryUp$}
\label{ch:concrete-instances-kleene-tree-boundary-namecert}
\origin{human}

Following Kleene's tree counterexample tradition and Bishop--Bridges constructive analysis, the $\KleeneTreeBoundaryUp$ packet records the finite boundary at which Kleene-tree prefix data, finite bar data, and completion-facing readbacks remain visible while branch selection and compactness principles stay refused. It is read after the prefix-tree carrier of \autoref{ch:concrete-instances-kleene-tree-namecert}, the binary prefix surface of \autoref{ch:concrete-instances-cantorspace-namecert}, the finite-bar discipline of \autoref{ch:concrete-instances-fantheorem-namecert}, the stream schedule of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real boundary of \autoref{ch:concrete-instances-real-namecert}. The packet isolates the constructive data a consumer may inspect before any illicit branch, open-cover compactness, countable choice, quotient stream equality, or $\RealUp$ completeness claim would be needed.

\begin{definition}[Kleene tree boundary carrier]
\label{def:kleene-tree-boundary-carrier}
A $\KleeneTreeBoundaryUp$ carrier is a finite $\BHist$ packet
$$
B=(K,F,S,R,E,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\KleeneTreeUp$ finite binary-prefix data, including the displayed tree ledger, node decisions, prefix spine, and obstruction row inherited from the Kleene-tree packet.
\item $F$ is the finite $\FanTheoremUp$ bar data used only as displayed finite bar and modulus-facing evidence.
\item $S$ is the $\StreamNameUp$ window schedule through which branch-facing prefix requests are read.
\item $R$ is the $\RegSeqRatUp$ readback row for rational observations routed through the same finite windows.
\item $E$ is the $\RealUp$ seal reached only after the prefix, bar, stream, and regular-rational rows have been displayed.
\item $O$ is the obstruction row refusing a selected branch, open-cover compactness, countable choice, quotient stream equality, and $\RealUp$ completeness as coordinates of the packet.
\item $H$ records componentwise $\hsame$ transport for the tree, bar, stream, regular-rational, real-seal, obstruction, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from finite stream windows through the Kleene prefix data and finite bar rows, then through the regular-rational readback and real seal to the obstruction row.
\item $P$ is the $\Pkg$ provenance over $\KleeneTreeBoundaryUp$, $\KleeneTreeUp$, $\CantorSpaceUp$, $\FanTheoremUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\KleeneTreeBoundaryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,F,S,R,E,O,H,C,P,N$. It has no coordinate for a completed infinite path, a Cantor-point selector, an open-cover compactness theorem, countable choice, quotient stream equality, or real completeness.
\end{definition}

\begin{theorem}[Kleene tree boundary NameCert obligations]
\label{thm:kleene-tree-boundary-namecert-obligations}
For every accepted $\KleeneTreeBoundaryUp$ carrier $B=(K,F,S,R,E,O,H,C,P,N)$, the local $\NameCert_{\KleeneTreeBoundaryUp}$ surface consists exactly of carrier admission, finite Kleene-prefix exposure, finite bar exposure, stream-window exposure, regular-rational readback, real-seal handoff, obstruction-row exposure, componentwise transport, displayed replay, provenance over the named dependency rows, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:kleene-tree-boundary-carrier}. The rows $K,F,S,R,E,O$ display the finite prefix, bar, stream, rational-readback, real-seal, and obstruction data that a consumer may inspect.

The structural rows $H$ and $C$ preserve this route componentwise. A request first enters through the finite $\StreamNameUp$ window $S$, then reads the Kleene-prefix row $K$ and the finite bar row $F$, then passes through $R$ and $E$ before reaching the obstruction row $O$.

The provenance and local name rows $P,N$ package exactly that finite route. Since the carrier contains no coordinate for a selected branch, open-cover compactness, countable choice, quotient stream equality, or $\RealUp$ completeness, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Kleene tree boundary finite bar refusal]
\label{thm:kleene-tree-boundary-finite-bar-refusal}
Every $\FanTheoremUp$, $\CantorSpaceUp$, $\RegSeqRatUp$, or $\RealUp$ consumer of an accepted $\KleeneTreeBoundaryUp$ packet factors through the finite rows $K,F,S,R,E,O,H,C,P,N$. The consumer may use the displayed finite prefix and bar data, but it cannot turn those rows into a selected branch, open-cover compactness, countable choice, quotient stream equality, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the finite-window route supplied by $S$. Each branch-facing request is replayed through a displayed prefix row in $K$ and a displayed finite bar row in $F$; no request reads an unlisted infinite path.

Next inspect the readback rows $R$ and $E$. They carry regular-rational and real-facing observations only after the finite prefix and bar evidence has already been displayed, so they cannot add a hidden selector or compactness principle.

Finally read the obstruction row $O$. Finite-row exhaustion leaves only the displayed route $K,F,S,R,E,O,H,C,P,N$, and $O$ explicitly refuses branch selection, open-cover compactness, countable choice, quotient stream equality, and real completeness as packet coordinates.
\end{proof}

\falsifiablePrediction{An accepted $\KleeneTreeBoundaryUp$ read is refuted if a consumer obtains a selected branch, open-cover compactness, countable choice, quotient stream equality, or $\RealUp$ completeness without displaying the finite Kleene-prefix row, finite bar row, stream window, regular-rational readback, real seal, obstruction row, transport, replay, provenance, and local naming row.}

\independenceWitness{KleeneTree, FanTheorem, StreamName, RegSeqRat, and Real: none is bijective to $\KleeneTreeBoundaryUp$ because the boundary packet jointly records finite prefix data, finite bar data, completion-facing readbacks, and an explicit obstruction row refusing branch selection and compactness principles.}

\closureat{KleeneTreeBoundaryUp}{seedStr}

\begin{closurestatus}{\KleeneTreeBoundaryUp}
  \constructivestory{A $\KleeneTreeBoundaryUp$ packet is generated from finite Kleene-tree prefix data, finite FanTheorem bar data, StreamName windows, RegSeqRat readbacks, a Real seal, an obstruction row, componentwise hsame transport, displayed continuation replay, package provenance, and local NameCert evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:kleene-tree-boundary-carrier}, \autoref{thm:kleene-tree-boundary-namecert-obligations}, and \autoref{thm:kleene-tree-boundary-finite-bar-refusal} seed the finite boundary separating Kleene-tree and bar evidence from branch selection, compactness, choice, quotient equality, and real completeness claims.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected branches, open-cover compactness, countable choice, quotient stream equality, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite prefix and bar exposure, readback and real-seal handoff, obstruction-row refusal, transport, replay, provenance, and local naming for BEDC.Derived.KleeneTreeBoundaryUp.}
\end{closurestatus}
