\chapter{A Concrete Naming Certificate for $\MooreSmithLTenCompletionNetUp$}
\label{ch:concrete-instances-moore-smith-l10-completion-net-namecert}
\origin{human}

Following Moore--Smith, Kelley, and Bourbaki on directed nets and completion by tails, the $\MooreSmithLTenCompletionNetUp$ packet records the finite L10 handoff by which a displayed Moore--Smith net completion route reaches the regular rational and real-name corridor. It sits after the directed-net carrier of \autoref{ch:concrete-instances-moore-smith-net-namecert}, the Cauchy-net completion boundary of \autoref{ch:concrete-instances-cauchynetcompletion-namecert}, the filter-base surface of \autoref{ch:concrete-instances-filterbase-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The chapter names a finite BEDC bridge object for Real and Completion consumers; it does not select limits, quotient nets, cofinal functions, ambient completions, host equalities, or completeness of $\RealUp$.

\begin{definition}[Moore--Smith L10 completion-net carrier]\label{def:moore-smith-l10-completion-net-carrier}
A $\MooreSmithLTenCompletionNetUp$ carrier is a finite $\BHist$ packet
$$
L=(D,T,F,W,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the directed-index row inherited from the accepted $\MooreSmithNetUp$ surface, including finite index vertices, displayed preorder comparisons, and common-upper witnesses.
\item $T$ is the tail-window row, recording the finite late-index requests and the displayed tails that answer completion-facing reads.
\item $F$ is the $\FilterBaseUp$ row generated from the displayed directed tails $D,T$.
\item $W$ is the $\CauchyNetCompletionUp$ row, exposing the same directed tail data as a Cauchy-net completion boundary.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the retained tail windows and tolerance reads.
\item $A$ is the terminal $\RealUp$ seal reached only after $D,T,F,W,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the directed-index, tail-window, filter-base, Cauchy-net completion, regular readback, real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a completion-net request through $D,T,F,W,R,A$.
\item $P$ is the $\Pkg$ provenance over $\MooreSmithLTenCompletionNetUp$, $\MooreSmithNetUp$, $\CauchyNetCompletionUp$, $\FilterBaseUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MooreSmithLTenCompletionNetUp}$ row.
\end{enumerate}
The carrier exports only this finite L10 route. It has no coordinate for selected limits, quotient nets, cofinal choice, ambient completion objects, host equality of completed values, or a completeness theorem for $\RealUp$.
\end{definition}

\begin{theorem}[Moore--Smith L10 completion-net NameCert obligations]\label{thm:moore-smith-l10-completion-net-namecert-obligations}
For an accepted $\MooreSmithLTenCompletionNetUp$ carrier $L=(D,T,F,W,R,A,H,C,P,N)$, the local $\NameCert_{\MooreSmithLTenCompletionNetUp}$ surface consists exactly of these finite obligation rows:
\begin{enumerate}
\item carrier admission for the directed-index, tail-window, filter-base, Cauchy-net completion, regular readback, real-seal, transport, replay, provenance, and local naming rows;
\item directed-tail coverage, requiring every completion-net request to consume $D$ and $T$ before $F,W,R,A$ can be inspected;
\item filter-base generation, requiring $F$ to be assembled only from the displayed directed tails;
\item Cauchy-net completion handoff, requiring $W$ to expose the same completion boundary consumed by \autoref{ch:concrete-instances-cauchynetcompletion-namecert};
\item regularization, requiring $R$ to be read before the terminal real seal $A$;
\item non-escape for selected limits, quotient nets, cofinal choice, ambient completion, host equality, and $\RealUp$ completeness.
\end{enumerate}
No local obligation is stored outside $D,T,F,W,R,A,H,C,P,N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:moore-smith-l10-completion-net-carrier}. The analytic rows are $D,T,F,W,R,A$, and the structural rows are $H,C,P,N$.

Directed-tail coverage comes first. A completion-net request reads a displayed index and late-window request through $D$ and $T$ before any filter, completion, regularization, or real-seal row can be used.

The filter-base and Cauchy-net obligations then use the sibling routes. The row $F$ is generated from the same directed tails, and $W$ exposes those tails as the Cauchy-net completion boundary consumed by the existing completion chapter.

Finally $R$ and $A$ provide the regular rational readback and terminal real seal. Transport and replay preserve the same route through $H$ and $C$, while $P,N$ name it as the local certificate surface. Since the excluded completion principles have no carrier coordinate, they cannot become local NameCert obligations.
\end{proof}

\begin{theorem}[Moore--Smith L10 regularization]\label{thm:moore-smith-l10-completion-net-regularization}
Every $\RegSeqRatUp$ read from an accepted $\MooreSmithLTenCompletionNetUp$ packet factors through the directed-tail and completion route
$$
D,T \longmapsto F,W \longmapsto R .
$$
Thus the regular rational row is attached to the same Moore--Smith tail windows and Cauchy-net completion boundary; it is not a separate sequence selector, quotient of nets, cofinal-choice schedule, or host-level limit name.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:moore-smith-l10-completion-net-namecert-obligations}. Directed-tail coverage forces every read of the packet to expose $D$ and $T$ before downstream rows are inspected.

Apply filter-base generation and Cauchy-net completion handoff. The rows $F$ and $W$ are downstream of the same displayed tails, so the regular readback cannot receive an independent source.

The row $R$ is therefore a readback of the retained finite route. The carrier inventory contains no sequence selector, quotient-net row, cofinal-choice function, or host limit coordinate, so the regularization is exhausted by $D,T,F,W,R$.
\end{proof}

\begin{theorem}[Moore--Smith L10 filter handoff]\label{thm:moore-smith-l10-completion-net-filter-handoff}
Every filter-facing consumer of an accepted $\MooreSmithLTenCompletionNetUp$ packet reads its $\FilterBaseUp$ data through the displayed Moore--Smith tail rows
$$
D,T \longmapsto F \longmapsto W,R,A,H,C,P,N .
$$
The handoff preserves the directed-net origin of the completion boundary and does not import an external filter, ultrafilter, quotient net, selected limit, or ambient completion object.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its only filter-facing coordinate is $F$, and the carrier definition presents $F$ as generated from $D$ and $T$.

The Cauchy-net completion and regularization rows are downstream of that same filter-base row. Thus a consumer that reaches $W,R,A$ has already passed through the displayed directed-tail route.

The structural rows do not add an external filter. They transport, replay, source, and name the same finite package, so no ultrafilter, quotient net, selected limit, or ambient completion object can bypass $D,T,F$.
\end{proof}

\begin{theorem}[Moore--Smith L10 real-seal nonescape]\label{thm:moore-smith-l10-completion-net-real-seal-nonescape}
Every $\RealUp$ seal read from an accepted $\MooreSmithLTenCompletionNetUp$ packet factors through
$$
D,T,F,W,R,A,H,C,P,N .
$$
The seal $A$ is terminal for the displayed L10 route only: it does not assert completeness of $\RealUp$, identify quotient-net representatives, select a limit, compare host real values, or provide a cofinal choice function.
\end{theorem}
\begin{proof}
Use the regularization theorem. By \autoref{thm:moore-smith-l10-completion-net-regularization}, every regular rational read reaches $R$ only after the directed tails, filter-base row, and Cauchy-net completion row have been displayed.

The real seal is downstream of that readback. The carrier definition gives $A$ as the terminal $\RealUp$ row after $D,T,F,W,R$, and the NameCert obligations leave no other route to a real-facing read.

It remains to exclude escape data. The packet has no coordinate for $\RealUp$ completeness, quotient-net representatives, selected limits, host equality, cofinal choice, or ambient completion, and $H,C,P,N$ preserve only the rows already displayed.
\end{proof}

\falsifiablePrediction{If a Real and Completion consumer reads a $\RealUp$ seal from a directed-net completion boundary without first displaying the $\MooreSmithNetUp$ tail row, the $\FilterBaseUp$ handoff, the $\CauchyNetCompletionUp$ boundary, and the $\RegSeqRatUp$ readback, it is not a $\MooreSmithLTenCompletionNetUp$ packet.}

\independenceWitness{moore-smith-net, cauchynetcompletion, filterbase, regseqrat, real: $\MooreSmithLTenCompletionNetUp$ is not bijective to any listed sibling because it binds directed tails, filter-base generation, Cauchy-net completion, regular rational readback, terminal real sealing, transport, replay, provenance, and local naming in one finite L10 route.}

\closureat{MooreSmithLTenCompletionNetUp}{seedStr}

\begin{closurestatus}{\MooreSmithLTenCompletionNetUp}
  \constructivestory{A $\MooreSmithLTenCompletionNetUp$ packet is generated from a MooreSmithNet directed-index row, finite tail-window data, a FilterBase handoff, a CauchyNetCompletion boundary, RegSeqRat readback, Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:moore-smith-l10-completion-net-carrier}, \autoref{thm:moore-smith-l10-completion-net-namecert-obligations}, \autoref{thm:moore-smith-l10-completion-net-regularization}, \autoref{thm:moore-smith-l10-completion-net-filter-handoff}, and \autoref{thm:moore-smith-l10-completion-net-real-seal-nonescape} seed the finite L10 completion-net handoff from Moore--Smith tails to regular rational readback and the real-name seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient nets, cofinal choice, ambient completion, host equality, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, directed-tail coverage, filter-base generation, Cauchy-net completion handoff, regularization, real-seal nonescape, transport preservation, and ledger refusal for BEDC.Derived.MooreSmithLTenCompletionNetUp.}
\end{closurestatus}
