\chapter{A Concrete Naming Certificate for $\EpigraphUp$}
\label{ch:concrete-instances-epigraph-namecert}
\origin{human}

Following Rockafellar's convex-analysis terminology, the $\EpigraphUp$ packet names the epigraph of a displayed extended-real-valued map as finite BEDC rows. It is read through domain points, function-value observations, lower-bound comparisons, and package provenance rather than through a host subset of a product space. The packet supplies the finite epigraph interface consumed by the lower-semicontinuity route of \autoref{ch:concrete-instances-lowersemicontinuous-namecert}, and its value and comparison rows terminate at the real-name boundary of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[Epigraph carrier]
\label{def:epigraph-carrier}
An $\EpigraphUp$ carrier is a finite $\BHist$ packet
$$
E=(D,V,L,O,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the domain-point row naming the source object and the inspected point.
\item $V$ is the function-value row, read through the relevant displayed value carrier and sealed at the $\RealUp$ boundary when a real comparison is requested.
\item $L$ is the lower-bound row naming the candidate ordinate for the epigraph inspection.
\item $O$ is the comparison row recording that the displayed lower bound is below the displayed value row.
\item $H$ stores componentwise $\hsame$ transport for the domain point, value, lower bound, comparison, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from an epigraph query through $D,V,L,O,H$.
\item $P$ is the $\Pkg$ provenance over $\EpigraphUp$, $\LowerSemicontinuousUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ dependency rows.
\item $N$ is the local $\NameCert_{\EpigraphUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. No coordinate stores a host graph, a powerset of a product, quotient equality of functions, a selected minimizing point, ambient real completeness, or an external lower-semicontinuity theorem.
\end{definition}

\begin{theorem}[Epigraph NameCert obligations]
\label{thm:epigraph-namecert-obligations}
For every accepted $\EpigraphUp$ carrier $E=(D,V,L,O,H,C,P,N)$, the local $\NameCert_{\EpigraphUp}$ surface consists exactly of carrier admission for the displayed rows, classifier comparison through the domain-point, value, lower-bound, and comparison rows, componentwise transport through $H$, lower-set exposure through the comparison row $O$, and ledger exactness through $C,P,N$. A consumer may inspect epigraph membership only after the domain point, function value, lower bound, and comparison rows are displayed, and the packet exports no host subset, graph quotient, selected minimizer, ambient completeness theorem, or hidden function-space equality.
\end{theorem}
\leanchecked{BEDC.Derived.EpigraphUp.EpigraphNameCertObligations}
\leanvariant{BEDC.Derived.EpigraphUp.EpigraphCarrier\_namecert\_obligations}
\begin{proof}
Project the carrier of \autoref{def:epigraph-carrier}. The only mathematical rows before the structural data are $D,V,L,O$, so carrier admission and classifier comparison must read the domain point, value, lower bound, and comparison directly.

The lower-set clause is exactly the comparison row $O$. Transport by $H$ preserves that comparison componentwise, while $C$ replays the same displayed route from an epigraph query to the visible rows.

The provenance and local naming rows $P,N$ source and name this finite packet. Since no carrier coordinate contains a host subset, graph quotient, selected minimizer, completeness theorem, or function-space equality, the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Epigraph lower-semicontinuity handoff]
\label{thm:epigraph-lower-semicontinuous-handoff}
Every $\LowerSemicontinuousUp$ consumer that reads open-sublevel or closed-superlevel obligations through an accepted $\EpigraphUp$ packet receives only the finite route
$$
D,V,L,O \longmapsto H,C,P,N.
$$
The handoff supplies the epigraph row consumed by the lower-semicontinuity certificate: a displayed domain point, a displayed value row, a lower-bound row, a comparison row, componentwise transport, replay, provenance, and local naming. It does not supply host open sets, a quotient graph, arbitrary function extensionality, selected witnesses, or ambient completeness of $\RealUp$.
\end{theorem}
\begin{proof}
Use \autoref{thm:epigraph-namecert-obligations}. It forces every epigraph membership read to expose $D,V,L,O$ before the structural rows may replay or source the answer.

Now pass to the $\LowerSemicontinuousUp$ consumer. The open-sublevel and closed-superlevel obligations read the epigraph-facing comparison as the finite row $O$, together with the value and lower-bound rows that make the comparison meaningful at the real-name boundary.

The structural rows $H,C,P,N$ preserve and name that route only. Because the carrier has no host topology, quotient graph, arbitrary function-extensional equality, selected witness coordinate, or ambient completeness field, the lower-semicontinuity consumer receives exactly the displayed epigraph packet.
\end{proof}

\falsifiablePrediction{An accepted $\EpigraphUp$ read is refuted if the comparison row $O$ is preserved while the displayed domain point $D$, value row $V$, and lower-bound row $L$ are removed.}

\independenceWitness{lowersemicontinuous, real: neither sibling is bijective with $\EpigraphUp$ because this packet jointly carries a domain-point row, function-value row, lower-bound row, comparison row, transport, replay, provenance, and local naming.}

\closureat{EpigraphUp}{seedStr}

\begin{closurestatus}{\EpigraphUp}
  \constructivestory{An $\EpigraphUp$ packet is generated from a domain-point row, a function-value row, a lower-bound row, a comparison row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:epigraph-carrier}, \autoref{thm:epigraph-namecert-obligations}, and \autoref{thm:epigraph-lower-semicontinuous-handoff} seed the finite epigraph interface for lower-semicontinuity consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host epigraph topology, quotient graphs, arbitrary function extensionality, selected minimizers, ambient real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier stability, lower-set exposure, ledger exactness, transport, replay, provenance, and local naming for BEDC.Derived.EpigraphUp.}
\end{closurestatus}
