\chapter{A Concrete Naming Certificate for $\PositiveInterpretabilityClassifierUp$}
\label{ch:concrete-instances-positive-interpretability-classifier-namecert}
\origin{ai}

The $\PositiveInterpretabilityClassifierUp$ packet realizes the certified-discovery and positive-cost-protocol surface of \autoref{sec:visions-philosophy-positive-interpretability-discovery} as finite classifier-shift, ledger, debt, and NameCert rows. It sits beside the classifier-shift witness of \autoref{ch:concrete-instances-classifier-novelty-witness-namecert}, the pipeline calculus of \autoref{ch:concrete-instances-discovery-pipeline-calculus-namecert}, the net-information packet of \autoref{ch:concrete-instances-explanation-complexity-information-namecert}, and the effective replacement ledger of \autoref{ch:concrete-instances-effective-replacement-ledger-namecert}. The packet classifies a discovery claim only after the changed classifier, cost protocol, debt profile, and local not-claimed boundary are all displayed.

\begin{definition}[Positive interpretability classifier carrier]
\label{def:positive-interpretability-classifier-carrier}
A $\PositiveInterpretabilityClassifierUp$ carrier is a finite $\BHist$ packet
$$
P=(E_0,E_1,J,\Delta,W,L,D,B,Q,H,C,R,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E_0$ is the source explanation-state row before the interpretability claim is classified.
\item $E_1$ is the target explanation-state row after the claim is classified.
\item $J$ is the $\ClassifierNoveltyWitnessUp$ row exposing a common source and a changed classifier judgment.
\item $\Delta$ is the classifier-shift row read by the discovery pipeline calculus.
\item $W$ is the public cost-protocol weight row for benefit, score, debt, source scope, target scope, and not-claimed boundary.
\item $L$ is the effective replacement ledger row recording which classifier and explanation rows have real downstream use.
\item $D$ is the explanation-debt row separating ledger, semantic, verification, intervention, and generalization debts.
\item $B$ is the benefit row for coverage, prediction, transfer, intervention, verification, and unification gains.
\item $Q$ is the $\ExplanationComplexityInformationUp$ net-information row comparing benefit against score and debt under $W$.
\item $H$ records componentwise $\hsame$ transport for $E_0,E_1,J,\Delta,W,L,D,B,Q$.
\item $C$ records displayed $\Cont$ replay through classifier-shift inspection, cost-protocol accounting, ledger lookup, debt exposure, benefit exposure, and net-information comparison.
\item $R$ is the $\Pkg$ provenance over $\PositiveInterpretabilityClassifierUp$, $\ClassifierNoveltyWitnessUp$, $\DiscoveryPipelineCalculusUp$, $\ExplanationComplexityInformationUp$, $\EffectiveReplacementLedgerUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PositiveInterpretabilityClassifierUp}$ row.
\end{enumerate}
The carrier has no coordinate for prose-only classifier novelty, ledger-only completion, raw score movement, hidden semantic truth, uncounted cost, undisplayed debt, or a positive discovery claim without the displayed classifier-shift row $J,\Delta$ and the cost-protocol row $W$.
\end{definition}

\begin{theorem}[Positive interpretability classifier NameCert obligations]
\label{thm:positive-interpretability-classifier-namecert-obligations}
For every accepted $\PositiveInterpretabilityClassifierUp$ carrier
$$
P=(E_0,E_1,J,\Delta,W,L,D,B,Q,H,C,R,N),
$$
the local $\NameCert_{\PositiveInterpretabilityClassifierUp}$ surface consists exactly of carrier admission for the two explanation states, classifier-novelty witness, classifier-shift row, public cost protocol, effective replacement ledger, debt row, benefit row, net-information row, componentwise transport, displayed replay, package provenance, and local naming. A positive interpretability classification is accepted only when $J,\Delta$ display classifier novelty and $Q$ reads $B,D,W,L$ under the same scope.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:positive-interpretability-classifier-carrier}. The classifier-shift surface is not implicit: the rows $J$ and $\Delta$ display the common source, changed judgment, and pipeline-facing shift.

Next read the cost protocol. The weight row $W$ fixes the scope and the benefit-score-debt accounting convention, while $L,D,B$ expose replacement use, debt, and benefit inside that scope.

The row $Q$ can classify the claim as positive only after those rows have been read together. This separates a true classifier shift with positive net information from ledger-only completion, formal hardening, raw score motion, or hidden semantic claims.

Finally, $H,C,R,N$ transport, replay, source, and name the same finite packet. Since none of the excluded objects appears in the carrier, the NameCert obligations are exactly the listed rows.
\end{proof}

\begin{theorem}[Positive interpretability falsifiable shift]
\label{thm:positive-interpretability-classifier-falsifiable-shift}
An accepted $\PositiveInterpretabilityClassifierUp$ consumer is refuted if it classifies a claim as positive interpretability discovery while any one of the classifier-shift rows $J,\Delta$, the public cost-protocol row $W$, the replacement ledger row $L$, the debt row $D$, the benefit row $B$, or the net-information row $Q$ is absent. Conversely, a ledger-only or formal-hardening improvement with unchanged classifier rows is not accepted by this classifier.
\end{theorem}
\begin{proof}
Apply \autoref{thm:positive-interpretability-classifier-namecert-obligations}. The obligations place classifier novelty and net-information accounting in the same carrier, so a consumer cannot obtain the positive classification from one side alone.

If $J$ or $\Delta$ is absent, the carrier has no displayed classifier shift. If $W,L,D,B,$ or $Q$ is absent, the carrier has no complete positive cost-protocol read.

The remaining rows $H,C,R,N$ preserve the same classification route under transport, replay, provenance, and local naming. Therefore a claim missing any named row is rejected, and a classifier-unchanged improvement is classified outside positive interpretability discovery.
\end{proof}

\falsifiablePrediction{Every accepted $\PositiveInterpretabilityClassifierUp$ positive-discovery read displays two explanation states, a classifier novelty witness, a classifier-shift row, a public cost protocol, effective replacement ledger rows, debt and benefit rows, net explanation information, transport, replay, provenance, and local NameCert naming.}

\independenceWitness{classifier-novelty-witness, explanation-complexity-information, discovery-pipeline-calculus, effective-replacement-ledger: none is bijective to $\PositiveInterpretabilityClassifierUp$ because this packet jointly carries the before-and-after explanation states, classifier-shift witness, public cost protocol, replacement ledger, debt accounting, benefit accounting, net-information comparison, transport, replay, provenance, and local naming as one classifier for positive interpretability discovery.}

The Lean follow-up must provide $\Nontrivial\ \PositiveInterpretabilityClassifierUp$ and $\FieldFaithful\ \PositiveInterpretabilityClassifierUp$ instances before checked markers for $\mathsf{BEDC.Derived.PositiveInterpretabilityClassifierUp}$ are cited. Those instances must preserve the rows $E_0,E_1,J,\Delta,W,L,D,B,Q,H,C,R,N$ so classifier novelty, ledger evidence, debt accounting, and positive net information remain separate fields.

\closureat{PositiveInterpretabilityClassifierUp}{seedStr}

\begin{closurestatus}{\PositiveInterpretabilityClassifierUp}
  \constructivestory{A $\PositiveInterpretabilityClassifierUp$ packet is generated from two explanation states, a classifier novelty witness, a classifier-shift row, public cost protocol weights, an effective replacement ledger, debt and benefit rows, net explanation information, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:positive-interpretability-classifier-carrier}, \autoref{thm:positive-interpretability-classifier-namecert-obligations}, and \autoref{thm:positive-interpretability-classifier-falsifiable-shift} seed the finite classifier for positive interpretability discovery claims.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close global interpretability quality, hidden semantic truth, prose-only classifier novelty, uncounted costs, undisplayed debts, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier-shift exactness, cost-protocol exposure, ledger and debt accounting, net-information comparison, transport, replay, provenance, local naming, and Nontrivial and FieldFaithful instances for BEDC.Derived.PositiveInterpretabilityClassifierUp.}
\end{closurestatus}
