\chapter{A Concrete Naming Certificate for $\HadamardFinitePartUp$}
\label{ch:concrete-instances-hadamard-finite-part-namecert}
\origin{human}

Following Hadamard's finite-part treatment of singular integrals and the constructive integration discipline of Bishop and Bridges, the $\HadamardFinitePartUp$ packet records a finite cutoff-and-subtraction certificate over the L10 Real and Completion surface. It sits after the Darboux and Riemann integration rows of \autoref{ch:concrete-instances-darbouxintegral-namecert} and \autoref{ch:concrete-instances-riemannintegral-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the bounded-variation control route of \autoref{ch:concrete-instances-boundedvariation-namecert}. The packet names only the finite singular window, the displayed subtraction row, rational readback, and Real seal handoff; it is not a measure completion, a principal-value host limit, a quotient-function construction, a selected limiting process, or an ambient real-completeness theorem.

\begin{definition}[Hadamard finite-part carrier]
\label{def:hadamard-finite-part-carrier}
A $\HadamardFinitePartUp$ carrier is a finite $\BHist$ packet
$$
F=(I,S,K,A,B,R,D,E,V,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the $\RealUp$ interval-source row, including the endpoint seals and the named singular location or finite singular subwindow.
\item $S$ is the singular-kernel row, recording the local pole order or displayed asymptotic term to be subtracted.
\item $K$ is the cutoff row, a finite family of excluded neighborhoods and retained compact subintervals.
\item $A$ is the subtraction row, displaying the finite counterterm or polynomial singular part removed on the retained windows.
\item $B$ is the Darboux or Riemann integration handoff row for the cutoff integrand on the retained finite partition.
\item $R$ is the $\RegSeqRatUp$ readback row for the cutoff-and-subtracted values.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger for the cutoff width, subtraction budget, rational readback, and Real seal comparison.
\item $E$ is the terminal $\RealUp$ seal row, public only after $K,A,B,R,D$ have been displayed.
\item $V$ is the $\BoundedVariationUp$ or variation-control row used to justify that the retained window remains a finite integration object.
\item $H$ stores componentwise $\hsame$ transport for $I,S,K,A,B,R,D,E,V$.
\item $C$ stores displayed $\Cont$ replay from a finite-part request through cutoff selection, subtraction, integration handoff, rational readback, tolerance comparison, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\HadamardFinitePartUp$, $\DarbouxIntegralUp$, $\RiemannIntegralUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BoundedVariationUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HadamardFinitePartUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these rows. No coordinate stores an ambient principal-value limit, measure completion, quotient function, chosen limiting sequence, host distribution object, or a proof that $\RealUp$ is complete.
\end{definition}

\begin{theorem}[Hadamard finite-part NameCert obligations]
\label{thm:hadamard-finite-part-namecert-obligations}
For every accepted $\HadamardFinitePartUp$ carrier $F=(I,S,K,A,B,R,D,E,V,H,C,P,N)$, the local $\NameCert_{\HadamardFinitePartUp}$ surface consists exactly of interval-source admission, singular-kernel exposure, finite cutoff visibility, subtraction-row exposure, Darboux or Riemann handoff, regular rational readback, dyadic tolerance accounting, Real seal routing, bounded-variation control, componentwise transport, displayed replay, package provenance, and local naming. A finite-part read is accepted only after the cutoff row $K$, subtraction row $A$, integration handoff $B$, readback row $R$, and tolerance ledger $D$ are all displayed.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hadamard-finite-part-carrier}. The interval row $I$ and singular-kernel row $S$ identify the singular site before any finite-part value can be read.

The cutoff and subtraction rows are then exposed. The row $K$ records the retained windows, while $A$ records the displayed singular term removed on those windows. The integration row $B$ is therefore a Darboux or Riemann handoff for a finite cutoff object rather than an ambient singular integral.

Next $R,D,E,V$ provide regular rational readback, tolerance accounting, the terminal Real seal, and bounded-variation control. Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since none of these rows contains a principal-value host limit, measure completion, quotient function, selected limiting sequence, distribution object, or ambient real-completeness proof, the listed rows exhaust the local obligations.
\end{proof}

\begin{theorem}[Hadamard finite-part cutoff nonescape]
\label{thm:hadamard-finite-part-cutoff-nonescape}
Every $\HadamardFinitePartUp$ consumer that reads an accepted carrier must factor its singular request through the finite route
$$
\RealUp,\ \BoundedVariationUp
\longmapsto
\DarbouxIntegralUp\ \hbox{or}\ \RiemannIntegralUp
\longmapsto
\RegSeqRatUp,\ \DyadicRatCoreUp
\longmapsto
\RealUp
$$
using the displayed rows $I,S,K,A,B,R,D,E,V,H,C,P,N$. In particular, deleting $K$ or $A$ leaves no public finite-part read.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:hadamard-finite-part-namecert-obligations}. They place the finite cutoff $K$ and subtraction row $A$ before the integration handoff and before any rational readback is available.

The Darboux or Riemann row $B$ can then be read only as the cutoff-and-subtracted integral surface. The rows $R$ and $D$ translate that surface into regular rational and dyadic tolerance data before the seal $E$ is public.

The structural rows $H,C,P,N$ preserve exactly that order. Without $K$ the retained finite window is absent; without $A$ the singular counterterm is absent. In either case the carrier has no coordinate from which a finite-part value can be exported.
\end{proof}

\begin{theorem}[Hadamard finite-part Real-seal handoff]
\label{thm:hadamard-finite-part-real-seal-handoff}
Every $\RealUp$-facing read exported by an accepted $\HadamardFinitePartUp$ packet reaches the Real seal $E$ only after the displayed cutoff row, subtraction row, integration handoff, regular rational readback, dyadic tolerance ledger, and bounded-variation control row have been consumed. The handoff supplies a finite singular-read certificate, not a measure completion, host principal-value limit, quotient-function equality, selected limit, or ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
By \autoref{def:hadamard-finite-part-carrier}, the only Real-facing output coordinate is $E$. The coordinate $E$ occurs after the cutoff, subtraction, integration, readback, tolerance, and variation-control rows in the displayed carrier.

Apply \autoref{thm:hadamard-finite-part-cutoff-nonescape}. Any consumer of $E$ must first traverse $K,A,B,R,D,V$ together with the structural rows. Therefore the Real seal is a terminal read of the finite certificate and not a host analytic limit.
\end{proof}

\falsifiablePrediction{Every accepted $\HadamardFinitePartUp$ singular read is refuted if a Real seal is cited without the displayed cutoff row, subtraction row, Darboux or Riemann handoff, RegSeqRat readback, DyadicRatCore tolerance ledger, and bounded-variation control row.}

\independenceWitness{darboux-integral, riemann-integral, regseqrat, dyadicratcore, real, bounded-variation: none is bijective to $\HadamardFinitePartUp$ because this packet jointly carries a singular-window row, cutoff row, subtraction row, integration handoff, rational readback, tolerance ledger, Real seal, variation-control row, transport, replay, provenance, and local naming as one finite-part certificate.}

\closureat{HadamardFinitePartUp}{seedStr}

\begin{closurestatus}{\HadamardFinitePartUp}
  \constructivestory{A $\HadamardFinitePartUp$ packet is generated from a Real interval source, singular-kernel row, finite cutoff row, subtraction row, Darboux or Riemann integration handoff, RegSeqRat readback, DyadicRatCore tolerance ledger, Real seal, bounded-variation control, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hadamard-finite-part-carrier}, \autoref{thm:hadamard-finite-part-namecert-obligations}, \autoref{thm:hadamard-finite-part-cutoff-nonescape}, and \autoref{thm:hadamard-finite-part-real-seal-handoff} seed the finite cutoff-and-subtraction route for Hadamard finite-part singular reads over the L10 Real and Completion surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close measure completion, principal-value host limits, quotient functions, selected limits, host distributions, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked interval-source admission, singular-kernel exposure, cutoff visibility, subtraction-row exposure, Darboux or Riemann handoff, RegSeqRat readback, DyadicRatCore tolerance accounting, Real seal routing, bounded-variation control, transport, replay, provenance, and local naming for BEDC.Derived.HadamardFinitePartUp.}
\end{closurestatus}
