\chapter{A Concrete Naming Certificate for $\BoundedMonotoneRealModulusUp$}
\label{ch:concrete-instances-bounded-monotone-real-modulus-namecert}
\origin{human}

Following Bishop and Bridges, a bounded monotone real-completion argument is useful only when each displayed positive tolerance yields a finite tail window before the completed real name is read. The $\BoundedMonotoneRealModulusUp$ packet records that tolerance-to-tail surface between the bounded monotone Cauchy witness of \autoref{ch:concrete-instances-boundedmonotonecauchywitness-namecert}, the convergence-seal boundary of \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. It names the finite modulus row consumed by Real and Completion-facing readers; it is not a selected-limit principle, a quotient stream equality, or an ambient completeness theorem.

\begin{definition}[Bounded monotone real modulus carrier]
\label{def:bounded-monotone-real-modulus-carrier}
A $\BoundedMonotoneRealModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(W,T,D,S,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $W$ is the accepted $\BoundedMonotoneCauchyWitnessUp$ source row, exposing the bounded monotone witness before any completion-facing read.
\item $T$ is the finite tail-modulus row assigning each displayed positive dyadic tolerance a tail-window bound for the same bounded monotone source.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, including positivity, halving, comparison, and upper-bound rows used by the tail request.
\item $S$ is the $\StreamNameUp$ window row exposed at the bound named by $T$.
\item $Q$ is the $\RegSeqRatUp$ handoff row reading the same finite window as regular rational approximation data.
\item $R$ is the terminal $\RealUp$ seal row reached only after $W,T,D,S,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for $W,T,D,S,Q,R$.
\item $C$ records displayed $\Cont$ replay from tolerance requests through tail bounds, finite windows, regular rational readbacks, the Real seal, and structural rows.
\item $P$ is the $\Pkg$ provenance over $\BoundedMonotoneRealModulusUp$, $\BoundedMonotoneCauchyWitnessUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BoundedMonotoneRealModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,T,D,S,Q,R,H,C,P,N$. It has no coordinate for selected limits, quotient stream equality, trichotomy, countable choice, host real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bounded monotone real modulus NameCert obligations]
\label{thm:bounded-monotone-real-modulus-namecert-obligations}
For every accepted $\BoundedMonotoneRealModulusUp$ carrier
$$
M=(W,T,D,S,Q,R,H,C,P,N),
$$
the local $\NameCert_{\BoundedMonotoneRealModulusUp}$ surface consists exactly of carrier admission through $M$, bounded monotone witness exposure through $W$, tail-modulus exposure through $T$, dyadic tolerance accounting through $D$, StreamName window exposure through $S$, RegSeqRat handoff through $Q$, terminal Real sealing through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$. No local obligation may select a limit, identify quotient streams, infer a tail bound without the dyadic tolerance row, bypass the finite window, invoke trichotomy or countable choice, or export ambient real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bounded-monotone-real-modulus-carrier}. Its analytic rows are precisely the bounded monotone witness, tail modulus, dyadic tolerance ledger, finite stream window, regular rational readback, and Real seal.

The tolerance request is public before the tail row is consumed. The row $D$ supplies the positive dyadic request and its comparison ledger, while $T$ answers with a finite tail-window bound for the same witness row $W$.

The rows $S$ and $Q$ then expose only the finite window and regular rational readback determined by that bound. The Real seal $R$ is downstream of those rows, so it cannot be used as an external completeness source.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since these structural rows add no selector, quotient, choice, trichotomy, host-real, compactness, or ambient-completeness coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Bounded monotone real Cauchy modulus]
\label{thm:bounded-monotone-real-cauchy-modulus}
Every accepted $\BoundedMonotoneRealModulusUp$ packet exposes, for each positive $\DyadicRatCoreUp$ tolerance read from $D$, a finite tail-window bound through $T$ before any $\RealUp$ row is readable. The corresponding $\StreamNameUp$ window $S$ and $\RegSeqRatUp$ handoff $Q$ are read at that bound, so the Cauchy-facing modulus is a finite route through
$$
W,D,T,S,Q \to R,H,C,P,N .
$$
\end{theorem}
\begin{proof}
Start with a positive dyadic tolerance in $D$. By the carrier definition, this request is part of the displayed tolerance ledger and is not inferred from the terminal Real seal.

Read the tail row $T$ next. It assigns the request to a finite tail-window bound for the same bounded monotone witness $W$; the construction therefore produces an explicit window before any Real-facing row can be consumed.

The rows $S$ and $Q$ replay that finite bound as a StreamName window and a RegSeqRat readback. The structural rows preserve the route under $\hsame$, $\Cont$, provenance, and local naming, while the excluded selector and quotient surfaces remain absent.
\end{proof}

\begin{theorem}[Bounded monotone real terminal seal]
\label{thm:bounded-monotone-real-terminal-seal}
Every completion-facing consumer of an accepted $\BoundedMonotoneRealModulusUp$ packet factors through $W,T,D,S,Q$ before the terminal $\RealUp$ row $R$ is readable. Consequently the packet exports a finite bounded-monotone tolerance-to-tail modulus and not a selected limit, quotient stream equality, trichotomy principle, countable-choice schedule, host real equality, open-cover compactness theorem, or ambient $\RealUp$ completeness proof.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bounded-monotone-real-modulus-namecert-obligations}. It fixes the order in which the bounded witness, tail modulus, dyadic tolerance ledger, stream window, and regular rational readback become available.

A completion-facing consumer can therefore read $R$ only after the finite modulus route has been displayed. If it omits one of $W,T,D,S,Q$, it asks for a Real seal coordinate without the carrier rows that make the seal local to the packet.

The structural rows $H,C,P,N$ do not add analytic content. They keep every read inside the named route, so the excluded limit, quotient, choice, trichotomy, host-real, compactness, and ambient-completeness surfaces remain outside the certificate.
\end{proof}

\falsifiablePrediction{A $\BoundedMonotoneRealModulusUp$ consumer that reads $\RealUp$ before displaying $W,T,D,S,Q$, or that exports selected limits, quotient stream equality, trichotomy, countable choice, host real equality, open-cover compactness, or ambient $\RealUp$ completeness, refutes the carrier of \autoref{def:bounded-monotone-real-modulus-carrier}.}

\independenceWitness{Nearest siblings: boundedmonotonecauchywitness, bounded-monotone-convergence-seal, dyadicratcore, streamname, regseqrat, and real. $\BoundedMonotoneRealModulusUp$ is not bijective to any one sibling because it jointly carries the bounded monotone witness, tolerance-to-tail row, dyadic ledger, finite stream window, regular rational readback, terminal Real seal, transport, replay, provenance, and local naming as one packet.}

\closureat{BoundedMonotoneRealModulusUp}{seedStr}

\begin{closurestatus}{\BoundedMonotoneRealModulusUp}
  \constructivestory{A $\BoundedMonotoneRealModulusUp$ packet is generated from a BoundedMonotoneCauchyWitness source row, a finite tail-modulus row, a DyadicRatCore tolerance ledger, a StreamName window row, a RegSeqRat readback row, a terminal RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bounded-monotone-real-modulus-carrier}, \autoref{thm:bounded-monotone-real-modulus-namecert-obligations}, \autoref{thm:bounded-monotone-real-cauchy-modulus}, and \autoref{thm:bounded-monotone-real-terminal-seal} seed the finite bounded-monotone tolerance-to-tail route before terminal Real reads.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected limits, quotient stream equality, trichotomy, countable choice, host real equality, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, bounded monotone witness exposure, tail-modulus exactness, dyadic tolerance accounting, StreamName window replay, RegSeqRat readback, terminal Real sealing, classifier transport, displayed replay, provenance, and local naming for BEDC.Derived.BoundedMonotoneRealModulusUp.}
\end{closurestatus}
