\chapter{A Concrete Naming Certificate for $\UniformCauchySubnetUp$}
\label{ch:concrete-instances-uniform-cauchy-subnet-namecert}
\origin{human}

Following Bishop-style constructive analysis, the $\UniformCauchySubnetUp$ packet records the finite modulus data by which a displayed regular sequence exposes a uniform subnet route for completion-facing consumers. It sits between the $\CauchyModulusUp$ tolerance surface, the finite-window discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the located-limit route of \autoref{ch:concrete-instances-locatedlimit-namecert}. The packet names a finite subnet modulus for displayed requests; it is not a countable-choice subsequence, a host subnet object, quotient stream equality, or ambient completeness for $\RealUp$.

\begin{definition}[Uniform Cauchy subnet carrier]
\label{def:uniform-cauchy-subnet-carrier}
A $\UniformCauchySubnetUp$ carrier is a finite $\BHist$ packet
$$
U=(S,M,W,D,R,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source regular sequence surface, read only through finite $\StreamNameUp$ windows.
\item $M$ is the $\CauchyModulusUp$ row assigning a displayed threshold to each dyadic precision request.
\item $W$ is the subnet-window ledger; for each displayed request it records the finite source windows and the finite subnet index comparisons needed for the request.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used by $M$ and $W$.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the scheduled windows and tolerances.
\item $E$ is the terminal $\RealUp$ seal reached only after $S,M,W,D,R$ have been read.
\item $L$ is the $\LocatedLimitUp$ handoff row exposing the same finite schedule as located-limit data.
\item $H$ records componentwise $\hsame$ transport for $S,M,W,D,R,E,L$.
\item $C$ records displayed $\Cont$ replay for source-window inspection, modulus lookup, subnet-window projection, dyadic tolerance comparison, regular rational readback, Real sealing, and located-limit handoff.
\item $P$ is the $\Pkg$ provenance over $\UniformCauchySubnetUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\LocatedLimitUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\UniformCauchySubnetUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $S,M,W,D,R,E,L,H,C,P,N$. It has no coordinate for countable choice, a selected infinite subsequence, a host subnet, quotient equality of streams, trichotomy, or ambient Real completeness.
\end{definition}

\begin{theorem}[Uniform Cauchy subnet NameCert obligations]
\label{thm:uniform-cauchy-subnet-namecert-obligations}
For every accepted $\UniformCauchySubnetUp$ carrier
$$
U=(S,M,W,D,R,E,L,H,C,P,N),
$$
the local $\NameCert_{\UniformCauchySubnetUp}$ surface consists exactly of carrier admission for the source sequence, modulus row, subnet-window ledger, dyadic tolerance row, regular rational readback, Real seal, located-limit handoff, componentwise transport, displayed replay, package provenance, and local naming. Every accepted consumer read must inspect $M$ and $D$ before reading a subnet window in $W$, must inspect $W$ before extracting $R$, and must pass through $R$ before consuming $E$ or $L$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:uniform-cauchy-subnet-carrier}. The only rows that can answer a precision request before readback are the modulus row $M$, the dyadic tolerance row $D$, and the subnet-window ledger $W$.

The proof is by induction over the displayed subnet requests. The base request reads the first stored tolerance, uses $M$ to locate the finite threshold, and then projects the matching source and subnet windows from $W$.

For the step, a stronger displayed request carries a refined dyadic tolerance in $D$. The same modulus row $M$ supplies a later threshold, and $W$ appends only the finite comparisons needed to show that the new subnet window lies beyond the previous one.

After each request has been projected, the readback row $R$ is determined by the scheduled windows and dyadic data. The Real seal $E$ and located-limit handoff $L$ are downstream of that readback, while $H,C,P,N$ transport, replay, source, and name the same finite route. Since the excluded choice, host-subnet, quotient, trichotomy, and completeness objects have no carrier coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Uniform Cauchy subnet RegSeqRat handoff]
\label{thm:uniform-cauchy-subnet-regseqrat-handoff}
Every completion-facing read from an accepted $\UniformCauchySubnetUp$ carrier factors through the displayed route
$$
\CauchyModulusUp,\ \StreamNameUp,\ \DyadicRatCoreUp,\ \RegSeqRatUp,\ \RealUp,\ \LocatedLimitUp .
$$
Concretely, the consumer first reads the source surface $S$, the modulus row $M$, the subnet-window ledger $W$, and the dyadic tolerance row $D$; it then obtains the $\RegSeqRatUp$ readback row $R$ and only afterward reaches the $\RealUp$ seal $E$ or the $\LocatedLimitUp$ handoff row $L$.
\end{theorem}
\begin{proof}
Start with the obligation package of \autoref{thm:uniform-cauchy-subnet-namecert-obligations}. It forces every precision request to expose $M,D,W$ before any regular rational readback is available.

Use finite-window projection on the displayed request. The stream windows in $W$ are not chosen by an external subsequence principle; they are the windows explicitly stored with the modulus threshold supplied by $M$ and the dyadic tolerance supplied by $D$.

The $\RegSeqRatUp$ row $R$ is then the only readback row available to the consumer. The terminal rows $E$ and $L$ read that same $R$, and the structural rows $H,C,P,N$ preserve the route under transport and replay. Thus the handoff reaches Real and located-limit consumers without exporting countable choice, a host subnet, quotient stream equality, trichotomy, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\UniformCauchySubnetUp$ completion read displays a CauchyModulus row, finite StreamName windows, DyadicRatCore tolerances, a RegSeqRat readback, a Real seal, a LocatedLimit handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming before it can be consumed by Real-completion or located-limit routes.}

\independenceWitness{cauchymodulus, streamname, regseqrat, dyadicratcore, real, locatedlimit: $\UniformCauchySubnetUp$ is not bijective to any listed sibling because it binds a uniform precision-to-window modulus, subnet-window comparisons, regular readback, Real sealing, and located-limit handoff in one finite packet.}

\closureat{UniformCauchySubnetUp}{seedStr}

\begin{closurestatus}{\UniformCauchySubnetUp}
  \constructivestory{A $\UniformCauchySubnetUp$ packet is generated from a displayed source sequence, a CauchyModulus row, a subnet-window ledger, DyadicRatCore tolerances, a RegSeqRat readback, a Real seal, a LocatedLimit handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-subnet-carrier}, \autoref{thm:uniform-cauchy-subnet-namecert-obligations}, and \autoref{thm:uniform-cauchy-subnet-regseqrat-handoff} seed the finite uniform subnet modulus route for completion-facing and located-limit consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close countable choice, selected host subsequences, quotient stream equality, trichotomy, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus exposure, subnet-window projection, dyadic tolerance accounting, regular readback, Real seal handoff, located-limit handoff, transport, replay, provenance, and local naming for BEDC.Derived.UniformCauchySubnetUp.}
\end{closurestatus}
