\chapter{A Concrete Naming Certificate for $\RealArctangentUp$}
\label{ch:concrete-instances-real-arctangent-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RealArctangentUp$ packet records arctangent as a finite Cauchy-stream certificate rather than as a host transcendental function. The construction reads the alternating arctangent series on bounded windows through $\RealAnalyticUp$ and the standalone $\RealSineUp$ trigonometric route of \autoref{ch:concrete-instances-real-sine-namecert}, then seals the endpoint through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$. It is placed beside the exponential and logarithm packets of \autoref{ch:concrete-instances-real-exponential-namecert} and \autoref{ch:concrete-instances-real-logarithm-namecert}: all three expose explicit real-analysis stream data before any public endpoint is consumed.

\begin{definition}[RealArctangent Cauchy carrier]
\label{def:real-arctangent-cauchy-carrier}
A $\RealArctangentUp$ carrier is a finite $\BHist$ packet
$$
A=(X,S,R,D,E,T,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\RealUp$ input row, read only through the displayed real-name boundary and bounded-window request.
\item $S$ is the alternating arctangent Cauchy stream row with inspected terms $(-1)^k x^{2k+1}/(2k+1)$ on the active bounded window.
\item $R$ is the $\RegSeqRatUp$ regularity row for the rational partial-sum readback of $S$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording denominator growth, bounded-window estimates, and alternating-remainder comparisons.
\item $E$ is the terminal $\RealUp$ endpoint seal reached only after the stream, regularity, and dyadic tolerance rows have been displayed.
\item $T$ is the $\RealAnalyticUp$ and $\RealSineUp$ transport row that identifies the local arctangent stream with the real-analytic trigonometric dependency surface, without importing a host inverse tangent.
\item $Q$ is the endpoint classifier row comparing accepted readbacks through the displayed $\RealUp$ boundary.
\item $H$ is the componentwise $\hsame$ transport for $X,S,R,D,E,T,Q,C,P,N$.
\item $C$ is the displayed $\Cont$ replay from bounded real input to stream windows, from windows to regular readback, from readback to dyadic tolerance, and from tolerance to the endpoint seal.
\item $P$ is the $\Pkg$ provenance over $\RealArctangentUp$, $\RealAnalyticUp$, $\RealSineUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RealArctangentUp}$ row.
\end{enumerate}
The classifier compares accepted arctangent packets only through $X,S,R,D,E,T,Q,H,C,P,N$. It has no coordinate for a host arctangent function, quotient real equality, analytic continuation, selected infinite sum, countable-choice schedule, unrestricted trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[RealArctangent NameCert obligations]
\label{thm:real-arctangent-namecert-obligations}
For every accepted $\RealArctangentUp$ carrier $A=(X,S,R,D,E,T,Q,H,C,P,N)$, the local $\NameCert_{\RealArctangentUp}$ surface consists exactly of carrier admission for the displayed packet; stream exposure through $S$ over the $\StreamNameUp$ finite-window route; regular readback through $R$; dyadic tolerance accounting through $D$; endpoint sealing through $E$ and $Q$; analytic and trigonometric dependency transport through $T$; componentwise $\hsame$ stability through $H$; displayed $\Cont$ replay through $C$; $\Pkg$ provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the accepted carrier. The only visible input, stream, regularity, tolerance, endpoint, dependency, classifier, transport, replay, provenance, and naming rows are $X,S,R,D,E,T,Q,H,C,P,N$.

The stream obligation is discharged by the finite windows in $S$ together with the regular readback $R$. The dyadic ledger $D$ records the bounded-window estimates and alternating-remainder comparisons needed before the endpoint row is available.

Use the dependency row $T$ to route the analytic and trigonometric material through $\RealAnalyticUp$ and $\RealSineUp$. This row is a displayed BEDC dependency route, not a host inverse-transcendental primitive.

Finally $E,Q,H,C,P,N$ seal, classify, transport, replay, source, and name exactly the same rows. Since no carrier coordinate stores a host arctangent, quotient real equality, analytic-continuation datum, selected infinite sum, countable-choice schedule, trichotomy oracle, or ambient completeness theorem, none of those objects is exported by the local NameCert surface.
\end{proof}

\begin{theorem}[RealArctangent stream dependency route]
\label{thm:real-arctangent-stream-dependency-route}
Every public read of an accepted $\RealArctangentUp$ packet factors through the concrete route
$$
\RealAnalyticUp,\quad
\RealSineUp,\quad
\StreamNameUp,\quad
\RegSeqRatUp,\quad
\DyadicRatCoreUp,\quad
\RealUp
$$
before an arctangent endpoint is consumed. Consequently the packet names arctangent by alternating Cauchy-stream data, regular rational readback, dyadic tolerance accounting, and real endpoint sealing, not by a host inverse tangent or an ambient analytic library.
\end{theorem}
\begin{proof}
Start from the carrier of \autoref{def:real-arctangent-cauchy-carrier}. The bounded real input $X$ and the stream row $S$ expose the arctangent partial sums only as finite $\StreamNameUp$ windows.

The readback and tolerance steps are $R$ and $D$. These rows place the partial sums inside the $\RegSeqRatUp$ and $\DyadicRatCoreUp$ surfaces before any endpoint classifier may be inspected.

The analytic dependency row $T$ ties the local alternating stream to $\RealAnalyticUp$ and the trigonometric route already isolated by $\RealSineUp$. It supplies a dependency handoff over existing siblings rather than a primitive host arctangent.

The endpoint rows $E,Q$ and structural rows $H,C,P,N$ then preserve and name the same route. Thus every public arctangent read factors through the displayed analytic, sine, stream, regular, dyadic, and real rows before the value is consumed.
\end{proof}

\falsifiablePrediction{Every $\RealArctangentUp$ public read factors through a bounded RealUp input row, alternating arctangent StreamName windows, RegSeqRat readback, a DyadicRatCore tolerance ledger, a RealAnalytic and RealSine dependency transport row, a RealUp endpoint seal, endpoint classifier, componentwise hsame transport, displayed continuation, package provenance, and local naming.}

\independenceWitness{real-analytic, real-sine, real-exponential, real-logarithm, streamname, regseqrat, dyadicratcore, real: $\RealArctangentUp$ is not bijective to any listed sibling because it jointly carries the alternating arctangent Cauchy stream, regular rational readback, dyadic tolerance ledger, analytic and trigonometric dependency transport, endpoint classifier, Real seal, transport, continuation, provenance, and local naming.}

\closureat{RealArctangentUp}{seedStr}

\begin{closurestatus}{\RealArctangentUp}
  \constructivestory{A $\RealArctangentUp$ packet is generated from a bounded RealUp input, alternating arctangent StreamName windows, RegSeqRat regular readback, a DyadicRatCore tolerance ledger, a RealAnalytic and RealSine dependency route, a RealUp endpoint seal, endpoint classifier, componentwise transport, displayed continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-arctangent-cauchy-carrier}, \autoref{thm:real-arctangent-namecert-obligations}, and \autoref{thm:real-arctangent-stream-dependency-route} seed the finite arctangent Cauchy-stream route through existing real, analytic, trigonometric, stream, regularity, and dyadic-tolerance surfaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host arctangent functions, quotient real equality, analytic continuation, selected infinite sums, countable choice, unrestricted trichotomy, ambient $\RealUp$ completeness, theorem-level Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, alternating stream exposure, regular readback, dyadic tolerance accounting, analytic and trigonometric dependency transport, endpoint classifier stability, and TasteGate field faithfulness for BEDC.Derived.RealArctangentUp.}
\end{closurestatus}
