\chapter{A Concrete Naming Certificate for $\InverseFunctionTheoremUp$}
\label{ch:concrete-instances-inverse-function-theorem-namecert}
\origin{human}

Following Cartan, Rudin, and Bishop--Bridges, the $\InverseFunctionTheoremUp$ packet records the theorem-level local inverse route exposed after a differentiable map, an invertible derivative row, a quantitative neighbourhood ledger, and the Real completion route have all been displayed. It sits above the local carrier boundary of \autoref{ch:concrete-instances-inverse-function-namecert}, consumes the Newton--Kantorovich theorem route of \autoref{ch:concrete-instances-newton-kantorovich-namecert} and the graph-window route of \autoref{ch:concrete-instances-implicitfunction-namecert}, and reaches observable endpoint data only through \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The packet names a finite BEDC route from displayed analytic hypotheses to a local inverse theorem certificate; it does not assert a host inverse theorem, select a germ, identify quotient function spaces, import ambient completeness, or provide bridge verification.

\begin{definition}[Inverse function theorem carrier]
\label{def:inverse-function-theorem-carrier}
An $\InverseFunctionTheoremUp$ carrier is a finite $\BHist$ packet
$$
T=(F,U,D,L,K,G,W,S,Q,R,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $F$ is the displayed map row together with the source and target classifier windows.
\item $U$ is the base-point and neighbourhood row, naming the point, value, source radius, target radius, and local domain of the theorem read.
\item $D$ is the derivative-control row over the displayed neighbourhood.
\item $L$ is the invertible-linear row for the derivative at the base point, including the finite inverse witness used by the quantitative route.
\item $K$ is the $\NewtonKantorovichUp$ row that supplies the contraction and root-existence certificate for nearby target values.
\item $G$ is the $\ImplicitFunctionUp$ graph-window row for the equation $F(x)-y=0$.
\item $W$ is the $\InverseFunctionUp$ local inverse-window row obtained from the same analytic and solving data.
\item $S$ is the $\StreamNameUp$ finite observation row for source, target, and endpoint windows.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational approximation data exposed by $S$.
\item $R$ is the terminal $\RealUp$ seal row for the theorem-facing completion route.
\item $H$ records componentwise $\hsame$ transport for all displayed analytic, solving, completion, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
F,U,D,L,K,G,W,S,Q,R \longmapsto \NameCert_{\InverseFunctionTheoremUp}.
$$
\item $P$ is the $\Pkg$ provenance over $\InverseFunctionTheoremUp$, $\InverseFunctionUp$, $\NewtonKantorovichUp$, $\ImplicitFunctionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\InverseFunctionTheoremUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,U,D,L,K,G,W,S,Q,R,H,C,P,N$. The carrier has no coordinate for a host theorem schema, selected inverse germ, quotient function-space equality, global bijection theorem, ambient Real completeness principle, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Inverse function theorem NameCert obligations]
\label{thm:inverse-function-theorem-namecert-obligations}
For every accepted $\InverseFunctionTheoremUp$ carrier
$$
T=(F,U,D,L,K,G,W,S,Q,R,H,C,P,N),
$$
the local $\NameCert_{\InverseFunctionTheoremUp}$ surface consists exactly of carrier admission for $T$, derivative-control exposure through $D$, invertible-linear exactness through $L$, Newton--Kantorovich solving through $K$, implicit graph-window handoff through $G$, local inverse-window handoff through $W$, stream observation through $S$, regular rational readback through $Q$, terminal Real sealing through $R$, componentwise $\hsame$ stability through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:inverse-function-theorem-carrier}. The analytic rows $F,U,D,L$ are the only source of map, neighbourhood, derivative, and invertibility data.

The solving rows are then forced. The Newton--Kantorovich row $K$ supplies the finite contraction route, the implicit-function row $G$ repacks the same equation as a graph window, and the inverse-function row $W$ exposes the resulting local inverse window.

The completion-facing rows come last. The stream row $S$ provides finite observations, $Q$ reads them as regular rational data, and $R$ seals the theorem-facing Real endpoint. The structural rows $H,C,P,N$ transport, replay, source, and name exactly this route, so no additional theorem schema, selected germ, quotient equality, global bijection, or ambient completeness coordinate is present.
\end{proof}

\begin{theorem}[Inverse function theorem Real completion route]
\label{thm:inverse-function-theorem-real-completion-route}
Every accepted $\InverseFunctionTheoremUp$ theorem read exported as a local inverse statement factors through the finite route
$$
\NewtonKantorovichUp \longmapsto \ImplicitFunctionUp \longmapsto \InverseFunctionUp \longmapsto \StreamNameUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
as instantiated by $K,G,W,S,Q,R$ and the analytic rows $F,U,D,L$. The Real-facing conclusion receives local window data, derivative and inverse-witness data, theorem-level solving data, finite observations, regular rational readback, terminal Real sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row; it receives no host inverse theorem, global inverse, selected germ, quotient function-space equality, or ambient completeness shortcut.
\end{theorem}
\begin{proof}
Start with the accepted carrier $T=(F,U,D,L,K,G,W,S,Q,R,H,C,P,N)$. The rows $F,U,D,L$ display the map, neighbourhood, derivative control, and invertible-linear witness before any theorem conclusion is read.

Apply the theorem-level solving route. The row $K$ gives the Newton--Kantorovich certificate, $G$ reads the same local equation as an implicit graph window, and $W$ opens the local inverse-window carrier from \autoref{ch:concrete-instances-inverse-function-namecert}.

Finally pass through the completion route. The stream, regular-rational, and Real rows $S,Q,R$ are read in that order, and $H,C,P,N$ preserve the same displayed path. Since no carrier coordinate stores a host inverse theorem, global inverse, selected germ, quotient function-space equality, or ambient completeness shortcut, the route is exhausted by the finite BEDC packet.
\end{proof}

\falsifiablePrediction{Every $\InverseFunctionTheoremUp$ theorem-facing read factors through one displayed map row, one neighbourhood row, one derivative-control row, one invertible-linear row, one NewtonKantorovich row, one ImplicitFunction row, one InverseFunction row, one StreamName finite-observation row, one RegSeqRat readback row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{inverse-function, newton-kantorovich, implicitfunction, streamname, regseqrat: $\InverseFunctionTheoremUp$ is not bijective to any listed sibling because it jointly carries theorem-level analytic hypotheses, Newton solving, implicit graph-window handoff, local inverse-window export, finite observation, regular rational readback, terminal Real sealing, transport, replay, provenance, and local naming as one certificate.}

\closureat{InverseFunctionTheoremUp}{seedStr}

\begin{closurestatus}{\InverseFunctionTheoremUp}
  \constructivestory{An $\InverseFunctionTheoremUp$ packet is generated from a displayed map row, base neighbourhood row, derivative-control row, invertible-linear row, NewtonKantorovich theorem row, ImplicitFunction graph-window row, InverseFunction local-window row, StreamName observations, RegSeqRat readbacks, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:inverse-function-theorem-carrier}, \autoref{thm:inverse-function-theorem-namecert-obligations}, and \autoref{thm:inverse-function-theorem-real-completion-route} seed the finite theorem-level local inverse route over analytic, solving, inverse-window, observation, regular rational, and Real completion rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host inverse theorems, global inverses, selected inverse germs, quotient function spaces, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, derivative-control exposure, invertible-linear exactness, Newton solving, implicit graph-window handoff, local inverse-window handoff, Real completion routing, provenance exactness, and local naming for BEDC.Derived.InverseFunctionTheoremUp.}
\end{closurestatus}
