\chapter{A Concrete Naming Certificate for $\LipschitzCompletionExtensionUp$}
\label{ch:concrete-instances-lipschitz-completion-extension-namecert}
\origin{human}

Following Bishop and Bridges on metric completion and Lipschitz extension, the $\LipschitzCompletionExtensionUp$ packet records the finite route by which a displayed Lipschitz map on a dense source row is handed to a completion target. It sits after the completion carrier of \autoref{ch:concrete-instances-completion-namecert}, the complete-metric boundary of \autoref{ch:concrete-instances-completemetric-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, and the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}. The packet is a completion-frontier NameCert surface; it is not a host extension theorem, a selected limit operation, quotient equality of completed points, countable choice, or ambient completeness imported from outside the displayed target seal.

\begin{definition}[Lipschitz completion extension carrier]
\label{def:lipschitz-completion-extension-carrier}
A $\LipschitzCompletionExtensionUp$ carrier is a finite $\BHist$ packet
$$
X=(D,M,L,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the dense source row, naming the source carrier, dense observation interface, and the finite source points on which the map is already displayed.
\item $M$ is the metric row, recording source and target distance readbacks, tolerance windows, and the metric comparison rows consumed by the extension route.
\item $L$ is the Lipschitz modulus row, listing the rational modulus bound, its tolerance rescalings, and the finite checks that transport source closeness into target closeness.
\item $S$ is the $\StreamNameUp$ row, exposing the finite source windows and target windows inspected by the route.
\item $Q$ is the $\RegSeqRatUp$ readback row for the source stream, target stream, distance budget, and modulus-scaled tolerance requests.
\item $E$ is the completion target seal, recording that the target-side Cauchy row is admitted only through the displayed completion boundary.
\item $H$ records componentwise $\hsame$ transport for the dense source, metric, modulus, stream-window, regular-rational, completion-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
D,M,L \longmapsto S,Q \longmapsto E .
$$
\item $P$ is the $\Pkg$ provenance over $\LipschitzCompletionExtensionUp$, $\CompletionUp$, $\CompleteMetricUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LipschitzCompletionExtensionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,M,L,S,Q,E,H,C,P,N$. It has no coordinate for a host extension operator, selected target limit, quotient equality of completed points, countable choice, global completeness of an ambient space, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Lipschitz completion extension NameCert obligations]
\label{thm:lipschitz-completion-extension-namecert-obligations}
For every accepted $\LipschitzCompletionExtensionUp$ carrier
$$
X=(D,M,L,S,Q,E,H,C,P,N),
$$
the local $\NameCert_{\LipschitzCompletionExtensionUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the dense source row, metric row, Lipschitz modulus row, StreamName windows, RegSeqRat readback, completion target seal, transport, replay, provenance, and local naming rows;
\item Lipschitz-modulus transport, requiring the rational bound and tolerance rescalings in $L$ to be read before any target closeness claim is exported;
\item dense-window handoff, requiring each source observation used by the extension request to pass through the finite $D,S,Q$ route;
\item completion target sealing, requiring the target-side Cauchy row to enter through $E$ after the displayed windows and regular rational readback are visible;
\item nonescape from selected limits or host completeness, requiring $H,C,P,N$ to transport, replay, source, and name only the rows $D,M,L,S,Q,E$.
\end{enumerate}
No Lipschitz completion extension obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:lipschitz-completion-extension-carrier}. The accepted packet displays the dense source, metric comparison, Lipschitz modulus, finite windows, regular rational readback, completion seal, and structural rows.

The modulus clause is read from $L$ together with the metric row $M$. A target closeness request must therefore cite the displayed rational Lipschitz bound and the tolerance rescalings before it can reach a target-side Cauchy claim.

The dense-window handoff is read from $D,S,Q$. The source observations are first exposed as dense rows, then inspected through finite StreamName windows, and then repacked as regular rational readback at the displayed tolerance.

The completion seal is read from $E$. The structural rows $H,C,P,N$ transport, replay, source, and name the same route, so the carrier contains no field where a selected limit, quotient equality, countable-choice schedule, host extension operator, or ambient completeness theorem could enter.
\end{proof}

\begin{theorem}[Lipschitz completion extension Cauchy handoff]
\label{thm:lipschitz-completion-extension-cauchy-handoff}
Let $X=(D,M,L,S,Q,E,H,C,P,N)$ be an accepted $\LipschitzCompletionExtensionUp$ carrier. Every Cauchy source stream routed through the displayed Lipschitz modulus yields a completion-target Cauchy row only through the finite route
$$
D,M,L \longmapsto S,Q \longmapsto E,H,C,P,N .
$$
The handoff supplies target Cauchy evidence for completion consumers without exporting a selected limit, quotient equality of completed points, countable choice, a host extension operator, or ambient completeness beyond the displayed completion target seal.
\end{theorem}
\begin{proof}
Start with a Cauchy source stream accepted by the dense source row. The stream is visible to the carrier only through $D$ and the finite windows $S$, so every source tolerance request is confined to the displayed dense-window route.

The metric row $M$ and Lipschitz modulus row $L$ rescale the source tolerance into the target tolerance. This step uses only the stored rational bound and its finite checks, not a host continuity theorem or a selected target value.

The row $Q$ reads the source and target windows as regular rational traces, and $E$ admits the target-side Cauchy row through the completion boundary. Finally $H,C,P,N$ preserve the same route as transport, replay, provenance, and local naming data. Since no other coordinate is present, any completion-target Cauchy handoff must pass through exactly these rows.
\end{proof}

\falsifiablePrediction{Every accepted $\LipschitzCompletionExtensionUp$ handoff from a dense source stream to a completion-target Cauchy row displays one dense source row, one metric row, one Lipschitz modulus row, one $\StreamNameUp$ window row, one $\RegSeqRatUp$ readback row, one completion target seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{completion, completemetric, streamname, regseqrat: no listed sibling supplies the joint finite packet containing dense source rows, metric comparison rows, Lipschitz modulus transport, finite source and target windows, regular rational readback, completion target sealing, transport, replay, provenance, and local NameCert.}

\closureat{LipschitzCompletionExtensionUp}{seedStr}

\begin{closurestatus}{\LipschitzCompletionExtensionUp}
  \constructivestory{A $\LipschitzCompletionExtensionUp$ packet is generated from dense source rows, metric comparison rows, Lipschitz modulus rows, StreamName windows, RegSeqRat readback, completion target seals, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:lipschitz-completion-extension-carrier}, \autoref{thm:lipschitz-completion-extension-namecert-obligations}, and \autoref{thm:lipschitz-completion-extension-cauchy-handoff} seed the finite route from dense-source Lipschitz data to completion-target Cauchy evidence.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, bridge checking, host Lipschitz extension theorems, selected target limits, quotient equality of completed points, countable choice, or ambient completeness outside the displayed completion target seal.}
  \upgradepath{Obligation closure requires checked carrier admission, Lipschitz-modulus transport, dense-window handoff, completion target sealing, Cauchy handoff replay, nonescape from selected limits or host completeness, transport, replay, provenance, and local naming for BEDC.Derived.LipschitzCompletionExtensionUp.}
\end{closurestatus}
