\chapter{A Concrete Naming Certificate for $\HyperbolicMobiusInvariantUp$}
\label{ch:concrete-instances-hyperbolic-mobius-invariant-namecert}
\origin{ai}

The $\HyperbolicMobiusInvariantUp$ packet realizes the boundary-fixed disk-transport reading of \autoref{ch:visions-hyperbolic-phase-geometry-observer-expansion} as finite Mobius-invariant rows. It sits after the disk carrier of \autoref{ch:concrete-instances-unitdisk-namecert}, the metric route of \autoref{ch:concrete-instances-hyperbolic-metric-namecert}, the Poincare disk metric packet of \autoref{ch:concrete-instances-poincare-disk-metric-namecert}, the hyperbolic cross-ratio packet of \autoref{ch:concrete-instances-hyperbolic-cross-ratio-namecert}, and the boundary-fixed transport route of \autoref{ch:concrete-instances-poincare-boundary-fixed-transport-namecert}. The packet names invariant preservation for displayed disk and boundary rows; it is not a completed hyperbolic plane, a quotient ideal boundary, a global automorphism group, or a physical observer law.

\begin{definition}[Hyperbolic Mobius invariant carrier]
\label{def:hyperbolic-mobius-invariant-carrier}
A $\HyperbolicMobiusInvariantUp$ carrier is a finite $\BHist$ packet
$$
I=(U,M,D,X,B,A,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\UnitDiskUp$ row for the source and target disk observations.
\item $M$ is the disk-map row recording the Mobius-style transport on displayed disk coordinates.
\item $D$ is the $\PoincareDiskMetricUp$ or $\HyperbolicMetricUp$ metric-read row consumed after the disk observations and transport have been exposed.
\item $X$ is the $\HyperbolicCrossRatioUp$ comparison row for boundary or near-boundary quadruple reads.
\item $B$ is the boundary-fixed row, recording which visible boundary source is preserved by the transport.
\item $A$ is the invariant audit row stating that the metric or cross-ratio read is preserved only through the displayed disk-map, boundary, and comparison rows.
\item $R$ is the terminal $\RealUp$ seal row attached to metric and cross-ratio readback.
\item $H$ records componentwise $\hsame$ transport for the displayed rows.
\item $C$ records displayed $\Cont$ replay of disk-coordinate, map, metric, cross-ratio, boundary, audit, Real-seal, provenance, and local-name reads.
\item $P$ is the $\Pkg$ provenance over $\HyperbolicMobiusInvariantUp$, $\UnitDiskUp$, $\PoincareDiskMetricUp$, $\HyperbolicMetricUp$, $\HyperbolicCrossRatioUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\HyperbolicMobiusInvariantUp}$ row.
\end{enumerate}
The carrier has no coordinate for a completed disk, quotient boundary, host automorphism group, selected geodesic, global compactification, or physical spacetime invariant.
\end{definition}

\begin{theorem}[Hyperbolic Mobius invariant NameCert obligations]
\label{thm:hyperbolic-mobius-invariant-namecert-obligations}
For every accepted $\HyperbolicMobiusInvariantUp$ carrier $I=(U,M,D,X,B,A,R,H,C,P,N)$, the local $\NameCert_{\HyperbolicMobiusInvariantUp}$ surface consists exactly of disk-coordinate admission, displayed Mobius-transport admission, hyperbolic metric readback, cross-ratio comparison, boundary-fixed preservation, invariant-audit exactness, Real sealing, componentwise transport, displayed replay, provenance, and local naming. The invariant row $A$ may be consumed only after $U,M,D,X,B$ have been displayed, and it exports no completed hyperbolic plane, quotient boundary, host automorphism group, global compactification, or physical observer law.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:hyperbolic-mobius-invariant-carrier}. The disk data $U$ and transport row $M$ are the only source rows from which the invariant route can begin.

The metric and cross-ratio reads are downstream. Rows $D$ and $X$ expose the finite comparison surfaces, while $B$ records the boundary-fixed source preserved by the displayed transport.

The audit row $A$ can therefore certify only preservation along that visible route. Rows $R,H,C,P,N$ seal, transport, replay, source, and name the same packet, and no excluded host geometry or physical law is present in the carrier.
\end{proof}

\falsifiablePrediction{Every accepted $\HyperbolicMobiusInvariantUp$ consumer must display UnitDisk coordinates, Mobius-style disk transport, HyperbolicMetricUp or PoincareDiskMetricUp metric reads, HyperbolicCrossRatioUp comparison, boundary-fixed preservation, invariant audit, RealUp sealing, hsame transport, Cont replay, Pkg provenance, and local NameCert rows before reading invariant preservation.}

\independenceWitness{unitdisk, hyperbolicmetric, poincare-disk-metric, hyperbolic-cross-ratio, poincare-boundary-fixed-transport: no listed sibling is bijective to $\HyperbolicMobiusInvariantUp$ because this packet jointly carries disk coordinates, Mobius-style transport, metric readback, cross-ratio comparison, boundary-fixed preservation, invariant audit, Real sealing, transport, replay, provenance, and local naming.}

\closureat{HyperbolicMobiusInvariantUp}{seedStr}

\begin{closurestatus}{\HyperbolicMobiusInvariantUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:hyperbolic-mobius-invariant-carrier} and \autoref{thm:hyperbolic-mobius-invariant-namecert-obligations} seed the finite Mobius-invariant disk-transport route over UnitDisk, hyperbolic metric, cross-ratio, boundary-fixed, Real-seal, transport, replay, provenance, and local NameCert rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close completed hyperbolic planes, quotient ideal boundaries, global automorphism groups, selected geodesics, physical observer laws, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked disk-coordinate admission, Mobius-transport admission, metric and cross-ratio exactness, boundary-fixed preservation, invariant audit nonescape, Real sealing, transport, replay, provenance, and local naming for BEDC.Derived.HyperbolicMobiusInvariantUp.}
  \constructivestory{A $\HyperbolicMobiusInvariantUp$ packet is generated from UnitDisk coordinates, displayed Mobius-style disk transport, PoincareDiskMetric or HyperbolicMetric reads, HyperbolicCrossRatio comparison, boundary-fixed preservation, an invariant audit row, RealUp sealing, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
