\chapter{A Concrete Naming Certificate for $\LocatedIntervalUniformCauchyUp$}
\label{ch:concrete-instances-located-interval-uniform-cauchy-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedIntervalUniformCauchyUp$ packet records the finite uniform-Cauchy surface for located compact intervals. It reads located endpoints through \autoref{ch:concrete-instances-locatedreal-namecert} and \autoref{ch:concrete-instances-locatedinterval-namecert}, interval containment through \autoref{ch:concrete-instances-bishop-compact-interval-namecert}, finite observations through \autoref{ch:concrete-instances-streamname-namecert}, rational readback through \autoref{ch:concrete-instances-regseqrat-namecert}, dyadic tolerance through \autoref{ch:concrete-instances-dyadicratcore-namecert}, and terminal sealing through \autoref{ch:concrete-instances-real-namecert}. The packet names a compact-interval uniform-Cauchy route as finite certificate data; it is not a Heine--Borel theorem, an open-cover compactness theorem, a quotient completion, a selected limit, or a choice principle.

\begin{definition}[Located interval uniform Cauchy carrier]
\label{def:located-interval-uniform-cauchy-carrier}
A $\LocatedIntervalUniformCauchyUp$ carrier is a finite $\BHist$ packet
$$
U=(L,I,K,W,R,D,M,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the $\LocatedRealUp$ endpoint row, carrying the lower and upper located real names used by the interval request.
\item $I$ is the $\LocatedIntervalUp$ row, exposing located containment and interval-membership data for the same endpoints.
\item $K$ is the $\BishopCompactIntervalUp$ row, read only as a finite compact-interval certificate surface for this displayed interval.
\item $W$ is the $\StreamNameUp$ finite-window row opened at the interval indices requested by $L,I,K$.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same finite windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row, recording the dyadic mesh, refinement, and comparison budget used by uniform-Cauchy reads.
\item $M$ is the uniform-Cauchy modulus row, requiring one dyadic tolerance budget to control all displayed interval windows accepted by $W$ and $R$.
\item $S$ is the terminal $\RealUp$ seal row reached only after the located endpoint, located interval, compact-interval, window, readback, tolerance, and uniform-Cauchy modulus rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for $L,I,K,W,R,D,M,S$.
\item $C$ records displayed $\Cont$ replay through the finite route
$$
L,I,K \longmapsto W,R,D,M \longmapsto S,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\LocatedIntervalUniformCauchyUp$, $\LocatedRealUp$, $\LocatedIntervalUp$, $\BishopCompactIntervalUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedIntervalUniformCauchyUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the displayed rows $L,I,K,W,R,D,M,S,H,C,P,N$. It has no coordinate for general Heine--Borel compactness, open-cover compactness, quotient completion equality, selected limits, countable choice, or host real equality.
\end{definition}

\begin{theorem}[Located interval uniform Cauchy NameCert obligations]
\label{thm:located-interval-uniform-cauchy-namecert-obligations}
For every accepted $\LocatedIntervalUniformCauchyUp$ carrier $U=(L,I,K,W,R,D,M,S,H,C,P,N)$, the local $\NameCert_{\LocatedIntervalUniformCauchyUp}$ surface consists exactly of located-real endpoint admission, located-interval containment admission, compact-interval certificate admission, finite StreamName window exposure, RegSeqRat readback, DyadicRatCore tolerance exactness, uniform-Cauchy modulus admission, Real seal admission, componentwise transport, displayed replay, provenance, and local naming for the same displayed rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-interval-uniform-cauchy-carrier}. The projection exposes the endpoint row, located interval row, compact-interval row, finite windows, rational readback, dyadic tolerance, uniform-Cauchy modulus, seal, and structural rows.

The endpoint and interval obligations are upstream of every uniform-Cauchy read. A consumer must first display $L,I,K$ before it can ask for the finite windows $W$ or the readback row $R$.

The dyadic tolerance row $D$ and modulus row $M$ then bind all accepted interval windows to one uniform request. The terminal seal $S$ is downstream of those rows, while $H,C,P,N$ transport, replay, source, and name the same packet.

Since the carrier has no coordinate for general compactness, quotient equality, selected limits, choice, or host real equality, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Located interval uniform Cauchy finite-net handoff]
\label{thm:located-interval-uniform-cauchy-finite-net-handoff}
Every finite-net consumer of an accepted $\LocatedIntervalUniformCauchyUp$ carrier factors through
$$
L,I,K \longmapsto W,R,D,M .
$$
The compact-interval row $K$ may hand off only the displayed located interval to the finite windows $W$, regular readback $R$, dyadic tolerance $D$, and uniform-Cauchy modulus $M$; it does not export an open-cover compactness theorem, a general Heine--Borel theorem, or a choice-selected net.
\end{theorem}
\begin{proof}
Start from the displayed carrier. The finite-net request has no source other than the located endpoint, located interval, and compact-interval rows $L,I,K$.

The window and readback rows are then read at the tolerances shown by $D$. The modulus row $M$ records that the same dyadic budget controls the displayed interval windows, so the finite-net handoff is a local route through $W,R,D,M$.

The structural rows preserve the same route. Because no row stores an open cover, a selected finite subcover, or a hidden choice schedule, the handoff is exactly the displayed finite-net route.
\end{proof}

\begin{theorem}[Located interval uniform Cauchy Real seal]
\label{thm:located-interval-uniform-cauchy-real-seal}
For every accepted $\LocatedIntervalUniformCauchyUp$ carrier $U=(L,I,K,W,R,D,M,S,H,C,P,N)$, the terminal $\RealUp$ seal $S$ can be consumed only after the located endpoint, located interval, compact-interval, finite-window, regular-readback, dyadic-tolerance, and uniform-Cauchy modulus rows have been displayed. The seal is therefore a local real-name endpoint for the packet, not a quotient completion, selected limit, ambient completeness theorem, or host real representative.
\end{theorem}
\begin{proof}
Read the carrier projection. The seal row $S$ appears after $L,I,K,W,R,D,M$, and the carrier lists no second real-facing coordinate.

Apply the NameCert obligation surface of \autoref{thm:located-interval-uniform-cauchy-namecert-obligations}. It forces window exposure, regular readback, dyadic tolerance exactness, and uniform-Cauchy modulus admission before the seal is public.

Finally use the non-escape content of the carrier: $H,C,P,N$ only transport, replay, source, and name the same finite packet. Thus a consumer may read $S$ only as the displayed terminal $\RealUp$ seal, not as any excluded completion, compactness, or choice object.
\end{proof}

\falsifiablePrediction{Every $\LocatedIntervalUniformCauchyUp$ read factors through located real endpoints, a located interval row, a compact interval row, finite StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a uniform-Cauchy modulus, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert.}

\independenceWitness{Nearest siblings: locatedreal, locatedinterval, compactinterval, streamname, regseqrat, dyadicratcore, and real. $\LocatedIntervalUniformCauchyUp$ is not bijective to any listed sibling because it jointly carries located endpoints, interval containment, compact-interval admission, finite windows, rational readback, dyadic tolerance, uniform-Cauchy control, Real sealing, transport, replay, provenance, and local naming as one packet.}

\closureat{LocatedIntervalUniformCauchyUp}{seedStr}

\begin{closurestatus}{\LocatedIntervalUniformCauchyUp}
  \constructivestory{A $\LocatedIntervalUniformCauchyUp$ packet is generated from LocatedReal endpoint rows, a LocatedInterval containment row, a CompactInterval certificate row, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a uniform-Cauchy modulus row, a RealUp seal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-interval-uniform-cauchy-carrier}, \autoref{thm:located-interval-uniform-cauchy-namecert-obligations}, \autoref{thm:located-interval-uniform-cauchy-finite-net-handoff}, and \autoref{thm:located-interval-uniform-cauchy-real-seal} seed the finite compact-interval uniform-Cauchy route over located endpoints, interval containment, compact-interval admission, finite windows, readback, tolerance, modulus, seal, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim general Heine--Borel compactness, open-cover compactness, quotient completion, selected limits, countable choice, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, located endpoint exactness, interval containment exactness, compact-interval admission, finite-window replay, RegSeqRat readback, dyadic tolerance exactness, uniform-Cauchy modulus exactness, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.LocatedIntervalUniformCauchyUp.}
\end{closurestatus}
