\chapter{A Concrete Naming Certificate for $\OsgoodModulusUp$}
\label{ch:concrete-instances-osgood-modulus-namecert}
\origin{human}

Following Osgood and Bishop--Bridges constructive ODE uniqueness, the $\OsgoodModulusUp$ packet records the finite modulus-divergence surface consumed by uniqueness criteria before an ODE solution comparison may reach a Real-facing seal. It sits beside the continuous-map carrier of \autoref{ch:concrete-instances-continuousmap-namecert}, the ODE row of \autoref{ch:concrete-instances-ode-namecert}, the Osgood uniqueness route of \autoref{ch:concrete-instances-osgood-uniqueness-namecert}, the Osgood criterion route of \autoref{ch:concrete-instances-osgood-criterion-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a finite divergence ledger for uniqueness consumers; it is not a host improper-integral theorem, a Lipschitz constant, a contraction ratio, a selected solution representative, or quotient equality of solution traces.

\begin{definition}[OsgoodModulus carrier]
\label{def:osgood-modulus-carrier}
An $\OsgoodModulusUp$ carrier is a finite $\BHist$ packet
$$
M=(O,V,A,T,Q,R,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the $\OdeUp$ source row, recording the time-state window and the uniqueness request that will consume the modulus data.
\item $V$ is the $\ContinuousMapUp$ vector-field row on the same ODE window, read as displayed continuity rather than as a host function.
\item $A$ is the modulus schedule row, listing positive $\RegSeqRatUp$ radius names, monotone comparison bounds, and the admissible near-zero window.
\item $T$ is the $\DyadicRatCoreUp$ tolerance row, recording dyadic scales, split radii, slack, and comparison witnesses used by the schedule.
\item $Q$ is the finite divergence ledger, recording reciprocal-modulus budget rows and lower-window checks rather than a host improper integral.
\item $R$ is the $\RegSeqRatUp$ readback row for the radius, budget, and solution-distance traces inspected by downstream consumers.
\item $L$ is the terminal $\RealUp$ seal reached only after $O,V,A,T,Q,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for ODE, continuous-map, schedule, tolerance, divergence, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
O,V \longmapsto A,T,Q \longmapsto R \longmapsto L .
$$
\item $P$ is the $\Pkg$ provenance over $\OsgoodModulusUp$, $\OdeUp$, $\ContinuousMapUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\OsgoodModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $O,V,A,T,Q,R,L,H,C,P,N$. It has no coordinate for a Lipschitz constant, contraction ratio, selected solution representative, host integral theorem, quotient equality of curves, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[OsgoodModulus NameCert obligations]
\label{thm:osgood-modulus-namecert-obligations}
For every accepted $\OsgoodModulusUp$ carrier
$$
M=(O,V,A,T,Q,R,L,H,C,P,N),
$$
the local $\NameCert_{\OsgoodModulusUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed ODE source, continuous vector-field, modulus schedule, dyadic tolerance, divergence ledger, regular readback, Real seal, transport, replay, provenance, and local naming rows;
\item ODE and continuity visibility, requiring $O$ and $V$ to be public before any modulus or divergence budget is read;
\item schedule exactness, requiring $A$ to display only positive $\RegSeqRatUp$ radius names, monotone comparison bounds, and the near-zero window used by the uniqueness consumer;
\item tolerance exactness, requiring $T$ to record every dyadic scale, split radius, slack, and comparison witness used by the displayed schedule;
\item divergence-ledger exactness, requiring $Q$ to store finite reciprocal-modulus budget rows and lower-window checks, not a host improper integral;
\item readback and seal nonescape, requiring $R,L,H,C,P,N$ to read, seal, transport, replay, source, and name only the displayed route.
\end{enumerate}
No Osgood modulus obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:osgood-modulus-carrier}. The accepted packet displays exactly the ODE source, continuous vector-field, modulus schedule, dyadic tolerance, divergence ledger, regular readback, Real seal, and structural rows.

The source and continuity clauses are read from $O,V$. A uniqueness-facing consumer therefore sees the ODE window and continuous vector-field row before it may inspect a modulus schedule or divergence budget.

The schedule and tolerance clauses are read from $A,T$. The schedule exposes positive regular-rational radius names, monotone comparison bounds, and the near-zero window, while the dyadic row records the scales and slack used by those comparisons.

The divergence and readback clauses are read from $Q,R,L$. The ledger $Q$ stores finite reciprocal-modulus budget checks, $R$ reads the radius and solution-distance traces, and $L$ seals the Real-facing boundary only after the displayed route is present. The structural rows $H,C,P,N$ transport, replay, source, and name that same route, so the carrier has no place to store the excluded host or choice data.
\end{proof}

\begin{theorem}[OsgoodModulus divergence handoff]
\label{thm:osgood-modulus-divergence-handoff}
Every uniqueness or criterion consumer of an accepted $\OsgoodModulusUp$ carrier must pass through
$$
\OdeUp,\ \ContinuousMapUp \longmapsto \RegSeqRatUp,\ \DyadicRatCoreUp,\ Q \longmapsto \RealUp
$$
as displayed by \autoref{def:osgood-modulus-carrier}. The consumer receives a finite divergence ledger and tolerance schedule for Osgood comparison, not a Lipschitz constant, contraction certificate, selected solution curve, host improper-integral theorem, or quotient equality of solution traces.
\end{theorem}
\begin{proof}
Begin with a uniqueness-facing consumer of $M$. The only source row is $O$, and the only vector-field row is $V$, so the consumer is confined to the displayed ODE window and continuous-map readback.

Next read the modulus rows. The row $A$ supplies the regular-rational radius schedule, $T$ supplies the dyadic tolerance arithmetic, and $Q$ supplies only finite reciprocal-modulus budget checks.

Finally read $R,L,H,C,P,N$. These rows provide regular readback, terminal Real sealing, componentwise transport, displayed replay, provenance, and local naming for the same route. Since no other coordinate is present, the handoff cannot export the excluded Lipschitz, contraction, selection, host-integral, quotient, choice, completeness, verification, or bridge data.
\end{proof}

\falsifiablePrediction{Every accepted $\OsgoodModulusUp$ uniqueness read that reaches $\RegSeqRatUp$ distance readback or a $\RealUp$ seal displays one $\OdeUp$ source row, one $\ContinuousMapUp$ vector-field row, one modulus schedule, one $\DyadicRatCoreUp$ tolerance row, one finite divergence ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.}

\independenceWitness{ode, continuousmap, osgood-uniqueness, osgood-criterion, regseqrat, dyadicratcore, real: no listed sibling supplies the joint finite packet containing an ODE source, continuous vector-field row, positive regular-rational radius schedule, dyadic tolerance row, divergence ledger, regular readback, Real seal, transport, replay, provenance, and local NameCert row.}

\closureat{OsgoodModulusUp}{seedStr}

\begin{closurestatus}{\OsgoodModulusUp}
  \constructivestory{An $\OsgoodModulusUp$ packet is generated from an OdeUp source row, a ContinuousMapUp vector-field row, a RegSeqRatUp radius schedule, a DyadicRatCoreUp tolerance row, a finite divergence ledger, RegSeqRatUp readback, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:osgood-modulus-carrier}, \autoref{thm:osgood-modulus-namecert-obligations}, and \autoref{thm:osgood-modulus-divergence-handoff} seed the finite Osgood modulus route from displayed ODE and ContinuousMap rows through regular-rational radius schedules, dyadic tolerance arithmetic, divergence ledgers, readback, and the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, Lipschitz uniqueness, Banach contraction, selected solution representatives, quotient equality of curves, countable choice, host improper-integral theorems, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, ODE-window visibility, continuous-map readback, modulus schedule exactness, dyadic tolerance exactness, divergence-ledger exactness, regular readback, Real-seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.OsgoodModulusUp.}
\end{closurestatus}
