\chapter{A Concrete Naming Certificate for $\StoneWeierstrassLatticeUp$}
\label{ch:concrete-instances-stone-weierstrass-lattice-namecert}
\origin{human}

Following Stone and Weierstrass, the $\StoneWeierstrassLatticeUp$ packet records the finite lattice-subalgebra route by which compact real-valued approximation can be read without selecting external dense families or importing an ambient function-space completion. It sits beside the separating-algebra certificate of \autoref{ch:concrete-instances-stone-weierstrass-namecert}, the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the continuous-name surface of \autoref{ch:concrete-instances-continuous-namecert}, the uniform-modulus handoff of \autoref{ch:concrete-instances-uniformmodulus-namecert}, and the real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The chapter names only displayed compact metric rows, continuous real-valued rows, lattice operations, separation evidence, finite approximation budgets, transport, replay, provenance, and a local certificate.

\begin{definition}[Stone--Weierstrass lattice carrier]
\label{def:stone-weierstrass-lattice-carrier}
A $\StoneWeierstrassLatticeUp$ carrier is a finite $\BHist$ packet
$$
L=(K,F,A,S,B,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact metric source row, including the named metric windows and finite compactness witnesses consumed by the approximation route.
\item $F$ is the continuous real-valued function row, reading each inspected target through the continuous chapter interface and the same $\RealUp$ windows used by the rest of the packet.
\item $A$ is the lattice subalgebra row. It displays constants, pointwise addition, pointwise multiplication, scalar multiplication, pointwise maximum, pointwise minimum, and the finite replay order by which these operations stay inside the named family.
\item $S$ is the separating-family evidence. For each displayed pair of apart compact metric names it records a member of $A$ and the finite real-window comparison that separates the pair.
\item $B$ is the finite approximation budget. It records the rational tolerance, the compact metric finite-net or finite-cover row used for that tolerance, and the finite list of lattice-subalgebra expressions inspected before the consumer accepts an approximation.
\item $R$ is the $\RealUp$ seal. Every value comparison, tolerance comparison, lattice operation output, and approximation error read passes through this row before it is exposed.
\item $H$ records componentwise $\hsame$ transport for compact metric source, continuous target, lattice operations, separating-family evidence, finite budget, real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact real-valued approximation request through $K,F,A,S,B,R,H$ and only then to provenance and naming.
\item $P$ is the $\Pkg$ provenance tying the packet to $\StoneWeierstrassLatticeUp$, $\StoneWeierstrassUp$, $\CompactMetricUp$, $\UniformModulusUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\StoneWeierstrassLatticeUp}$ row.
\end{enumerate}
Accepted carriers are compared only through these rows. There is no coordinate for classical choice, arbitrary function equality, measure completion, a selected dense sequence, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Stone--Weierstrass lattice NameCert obligations]
\label{thm:stone-weierstrass-lattice-namecert-obligations}
For every accepted $\StoneWeierstrassLatticeUp$ carrier
$$
L=(K,F,A,S,B,R,H,C,P,N),
$$
the local $\NameCert_{\StoneWeierstrassLatticeUp}$ surface consists exactly of compact metric source admission, continuous real-valued target admission, lattice subalgebra operation visibility, separating-family evidence, finite approximation budget admission, $\RealUp$ sealing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming.
\end{theorem}
\begin{proof}
Project the rows of \autoref{def:stone-weierstrass-lattice-carrier}. The compact metric source is stored in $K$, while the inspected real-valued continuous target is stored in $F$.

The algebraic and lattice closure obligations are exactly the row $A$. The separating-family obligations are exactly the row $S$, and every accepted approximation request must pass through the finite budget row $B$.

The real-name boundary is fixed by $R$. Transport, replay, provenance, and naming are then supplied by $H,C,P,N$. Since the carrier has no other coordinates, the listed obligations exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Stone--Weierstrass lattice uniform approximation route]
\label{thm:stone-weierstrass-lattice-uniform-approximation-route}
Every approximation-facing consumer of an accepted $\StoneWeierstrassLatticeUp$ carrier factors through the finite route
$$
K,F \longmapsto A,S \longmapsto B,R \longmapsto H,C,P,N .
$$
Thus the consumer receives a compact metric source, a continuous real-valued target, displayed lattice-subalgebra operations, separating-family evidence, a finite approximation budget, a $\RealUp$ seal, transport, replay, provenance, and local naming; it receives no selected subsequence, open-ended function equality test, measure completion, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with an approximation-facing read of the accepted carrier. The request first reaches $K$ and $F$, so the source and target are the displayed compact metric and continuous real-valued rows.

The request then reads lattice operations from $A$ and separation data from $S$. These rows supply only finite expressions and finite real-window comparisons.

The finite budget row $B$ selects the displayed tolerance and compact witness used by the consumer, while $R$ seals every comparison through $\RealUp$. The structural rows $H,C,P,N$ preserve the same route, so the excluded principles cannot be recovered from the packet.
\end{proof}

\begin{theorem}[Stone--Weierstrass lattice real-seal nonescape]
\label{thm:stone-weierstrass-lattice-real-seal-nonescape}
In an accepted $\StoneWeierstrassLatticeUp$ carrier, every value read, lattice-operation output, separating comparison, tolerance comparison, and approximation-error claim reaches downstream consumers through the displayed $\RealUp$ seal row $R$. Consequently no downstream consumer can use the packet to claim classical choice, arbitrary function equality, measure completion, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Inspect the carrier route. Value reads and operation outputs are produced by $F$ and $A$, but they are not exported until $R$ records the corresponding real-name windows.

Separating comparisons and approximation-error claims are produced by $S$ and $B$. Those rows also feed their real comparisons through $R$ before replay reaches the public naming rows.

The remaining rows $H,C,P,N$ transport and name only the already sealed route. Since no excluded principle is a coordinate of $L$, and no replay edge bypasses $R$, the real-seal boundary is nonescaping.
\end{proof}

\falsifiablePrediction{Every accepted $\StoneWeierstrassLatticeUp$ approximation-facing read factors through compact metric rows, continuous real-valued target rows, displayed lattice-subalgebra operations, separating-family evidence, a finite approximation budget, a $\RealUp$ seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{stone-weierstrass, compactmetric, continuous, uniformmodulus, real: $\StoneWeierstrassLatticeUp$ is not bijective to any listed sibling because it jointly carries lattice-subalgebra closure, separating-family evidence, compact metric approximation budgets, real sealing, transport, replay, provenance, and local naming.}

\closureat{StoneWeierstrassLatticeUp}{seedStr}

\begin{closurestatus}{\StoneWeierstrassLatticeUp}
  \constructivestory{A $\StoneWeierstrassLatticeUp$ packet is generated from compact metric source rows, continuous real-valued target rows, displayed lattice-subalgebra operations, separating-family evidence, finite approximation budgets, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stone-weierstrass-lattice-carrier}, \autoref{thm:stone-weierstrass-lattice-namecert-obligations}, \autoref{thm:stone-weierstrass-lattice-uniform-approximation-route}, and \autoref{thm:stone-weierstrass-lattice-real-seal-nonescape} seed the compact real-valued lattice approximation route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close classical choice, arbitrary function equality, measure completion, ambient RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, lattice-operation visibility, separating-family exactness, finite-budget routing, real-seal nonescape, and uniform approximation route proofs for BEDC.Derived.StoneWeierstrassLatticeUp.}
\end{closurestatus}
