\chapter{A Concrete Naming Certificate for $\LocatedLowerBoundUp$}
\label{ch:concrete-instances-located-lower-bound-namecert}
\origin{human}

Following Bishop--Bridges constructive analysis, the $\LocatedLowerBoundUp$ packet isolates the finite lower-bound witness that located infimum and compact-minimum arguments may inspect before any ambient completeness or selected minimum principle is available. It is the order-dual reusable face to the $\LocatedUpperBoundUp$ packet of \autoref{ch:concrete-instances-located-upper-bound-namecert}, feeds the infimum route of \autoref{ch:concrete-instances-locatedinfimum-namecert}, and keeps its readback tied to the located-real, regular-rational, and real-name surfaces of \autoref{ch:concrete-instances-locatedreal-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. The chapter names lower-bound data as a finite NameCert carrier, not as Real completeness, trichotomy, quotient cuts, selected extrema, or a host order oracle.

\begin{definition}[Located lower-bound carrier]
\label{def:located-lower-bound-carrier}
A $\LocatedLowerBoundUp$ carrier is a finite $\BHist$ packet
$$
B=(F,L,W,R,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $F$ is the located source row, read through the $\LocatedRealUp$ surface and its displayed comparison windows;
\item $L$ is the lower-bound comparison ledger, recording the finite rows that place the proposed lower surface below each inspected source value;
\item $W$ is the $\StreamNameUp$ request schedule that fixes the finite precision windows in which source and lower-bound comparisons are inspected;
\item $R$ is the $\RegSeqRatUp$ readback row that repacks the scheduled comparison observations as regular rational data;
\item $E$ is the terminal $\RealUp$ seal reached only after $F,L,W,R$ have been displayed;
\item $H$ records componentwise $\hsame$ transport for the located source, lower-bound ledger, window schedule, regular readback, Real seal, replay, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ routes for lower-bound reads, regular-rational handoff, Real-seal readback, and downstream located-infimum replay;
\item $P$ is the $\Pkg$ provenance over $\LocatedLowerBoundUp$, $\LocatedUpperBoundUp$, $\LocatedInfimumUp$, $\LocatedRealUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LocatedLowerBoundUp}$ row.
\end{enumerate}
The carrier has no row for Real completeness, trichotomy, quotient-cut equality, a selected minimum, an arbitrary infimum operator, countable choice, or host-level order evaluation.
\end{definition}
\leandef{BEDC.Derived.LocatedLowerBoundUp}

\begin{theorem}[Located lower-bound NameCert obligations]
\label{thm:located-lower-bound-namecert-obligations}
For every accepted $\LocatedLowerBoundUp$ carrier $B=(F,L,W,R,E,H,C,P,N)$, the local $\NameCert_{\LocatedLowerBoundUp}$ surface consists exactly of carrier admission for the displayed packet, source exposure through $F$, lower-bound comparison exactness through $L$, finite request-window compatibility through $W$, regular-rational readback through $R$, terminal Real-seal routing through $E$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-lower-bound-carrier}. The analytic rows are precisely $F,L,W,R,E$, and the structural rows are precisely $H,C,P,N$.

Carrier admission and source exposure read $F$ before any comparison is consumed. Lower-bound comparison exactness then reads only the displayed entries of $L$ inside the request schedule fixed by $W$.

The regular-rational and Real-facing obligations are downstream from that schedule. The row $R$ repacks the inspected comparisons, and $E$ seals the Real-facing read only after $F,L,W,R$ have been exposed.

The remaining rows preserve the same packet. The transports in $H$, replays in $C$, provenance in $P$, and local name $N$ add no completeness principle, trichotomy row, quotient-cut equality, selected extremum, or host order evaluator.
\end{proof}

\begin{theorem}[Located lower-bound Real seal route]
\label{thm:located-lower-bound-real-seal-route}
Every $\RealUp$-facing consumer of an accepted $\LocatedLowerBoundUp$ carrier receives the finite route
$$
F,L,W,R,E,H,C,P,N .
$$
The consumer must read the located source row, the lower-bound comparison ledger, the request schedule, and the regular-rational readback before the terminal Real seal is available. The route is stable under the displayed $\hsame$ and $\Cont$ rows, and it exports no Real completeness, trichotomy, quotient cut, selected minimum, arbitrary infimum operator, countable choice, or host order evaluation.
\end{theorem}
\begin{proof}
Start with an accepted carrier $B=(F,L,W,R,E,H,C,P,N)$. By \autoref{thm:located-lower-bound-namecert-obligations}, any Real-facing read must first expose the located source, lower-bound ledger, finite request window, and regular readback rows.

The terminal row $E$ is therefore downstream from $F,L,W,R$. A consumer that has not read those rows has no coordinate from which to obtain a Real-facing lower-bound certificate.

Transport and replay do not enlarge the route. The rows $H$ and $C$ preserve the displayed packet through componentwise sameness and continuation replay, while $P,N$ source and name the same finite data.

Thus the Real-seal route is exactly $F,L,W,R,E,H,C,P,N$, with the listed excluded principles absent from the carrier.
\end{proof}

\begin{closurestatus}{\LocatedLowerBoundUp}
  \constructivestory{A $\LocatedLowerBoundUp$ packet is generated from a located source row, a lower-bound comparison ledger, a StreamName request schedule, a RegSeqRat readback row, a RealUp seal, componentwise hsame transport, displayed Cont replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-lower-bound-carrier}, \autoref{thm:located-lower-bound-namecert-obligations}, and \autoref{thm:located-lower-bound-real-seal-route} seed the reusable lower-bound face for located infimum and compact-minimum consumers over the L10 Real route.}
  \formalstatus{\encodedDefV}
  \leantarget{BEDC.Derived.LocatedLowerBoundUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Real completeness, trichotomy, quotient-cut equality, selected extrema, arbitrary infima, countable choice, host order evaluation, or a standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, lower-bound comparison exactness, request-window compatibility, regular readback, Real-seal routing, transport, replay, provenance, and local naming for the displayed packet.}
\end{closurestatus}
