\chapter{A Concrete Naming Certificate for $\LocatedIntervalSupremumUp$}
\label{ch:concrete-instances-located-interval-supremum-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\LocatedIntervalSupremumUp$ packet records the finite interval-restricted route by which a located supremum read becomes available over a displayed real interval. It sits over the upper-bound and lower-approximation surface of \autoref{ch:concrete-instances-locatedsupremum-namecert}, the retained-branch discipline of \autoref{ch:concrete-instances-located-interval-bisection-namecert}, the bounded interval completion boundary of \autoref{ch:concrete-instances-bounded-complete-real-interval-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names constructive interval supremum data as finite rows; it does not assert general $\RealUp$ completeness, open-cover compactness, trichotomy, countable choice, quotient real equality, or a selected host supremum.

\begin{definition}[Located interval supremum carrier]
\label{def:located-interval-supremum-carrier}
A $\LocatedIntervalSupremumUp$ carrier is a finite $\BHist$ packet
$$
I=(J,U,A,B,W,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $J$ is the located interval source row. It records the displayed endpoints, interval membership requests, and interval-local locatedness data consumed before any supremum-facing read is accepted.
\item $U$ is the upper-bound ledger. It records that the candidate Real-facing row bounds the interval-local family through displayed endpoint, membership, and tolerance checks.
\item $A$ is the lower-approximation ledger. For each accepted precision request it displays an interval-local approximation row that lies below the bound surface and is read through the same precision route.
\item $B$ is the bisection and refinement row. It records retained subintervals, branch decisions, and diameter or tolerance refinements supplied by the located interval bisection surface.
\item $W$ is the finite $\StreamNameUp$ window opened at the indices and tolerances displayed by $J,U,A,B$.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same finite windows and dyadic tolerance data.
\item $E$ is the terminal $\RealUp$ seal, consumed only after the interval source, upper-bound ledger, lower-approximation ledger, refinement row, finite windows, and regular readback have been displayed.
\item $H$ records componentwise $\hsame$ transport for $J,U,A,B,W,R,E,C,P,N$.
\item $C$ records displayed $\Cont$ replay for interval-supremum requests through the finite route
$$
J,U,A,B \longmapsto W,R \longmapsto E,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\LocatedIntervalSupremumUp$, $\LocatedSupremumUp$, $\LocatedIntervalBisectionUp$, $\BoundedCompleteRealIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedIntervalSupremumUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $J,U,A,B,W,R,E,H,C,P,N$. It has no coordinate for a selected host supremum, quotient real equality, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located interval supremum NameCert obligations]
\label{thm:located-interval-supremum-namecert-obligations}
For every accepted $\LocatedIntervalSupremumUp$ carrier $I=(J,U,A,B,W,R,E,H,C,P,N)$, the local $\NameCert_{\LocatedIntervalSupremumUp}$ surface is exhausted by the following finite obligations:
\begin{enumerate}
\item carrier admission for the located interval source, upper-bound ledger, lower-approximation ledger, bisection and refinement row, finite StreamName window, RegSeqRat readback, Real seal, transport, replay, provenance, and local naming rows;
\item upper-bound exposure, requiring every supremum-facing bound read to display $J$ and $U$ before $E$ can be consumed;
\item lower-approximation cofinality, requiring each accepted precision request to receive an approximation row in $A$ through the same interval and window route;
\item bisection-window exactness, requiring the retained subinterval and refinement data in $B$ to determine the windows opened in $W$;
\item readback and seal handoff, requiring each Real-facing read to pass through $W,R,E$ after the interval source, bound, approximation, and bisection rows have been displayed;
\item componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming through $H,C,P,N$.
\end{enumerate}
No obligation exports a selected host supremum, quotient real equality, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:located-interval-supremum-carrier}. The projection exposes exactly the located interval source $J$, the upper-bound ledger $U$, the lower-approximation ledger $A$, the bisection and refinement row $B$, the finite observation rows $W,R$, the terminal seal $E$, and the structural rows $H,C,P,N$.

The upper and lower supremum faces are row-local. A bound read must use $J$ and $U$, while a precision request for lower approximation must use $A$ over the same interval source. Since both faces are tied to $B$, the retained branch and refinement data determine which finite windows are opened.

The Real-facing handoff is then forced through $W,R,E$. The StreamName row supplies only the displayed finite windows, the RegSeqRat row supplies the regular rational readback attached to those windows, and the Real seal is downstream of that readback.

Finally the structural rows transport, replay, source, and name the same finite route. Because the carrier contains no row for a selected host supremum, quotient equality, choice schedule, trichotomy decision, open-cover subcover, or ambient completeness theorem, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Located interval supremum Real seal route]
\label{thm:located-interval-supremum-real-seal-route}
Every Real-facing supremum read exported by an accepted $\LocatedIntervalSupremumUp$ carrier
$$
I=(J,U,A,B,W,R,E,H,C,P,N)
$$
factors through the finite route
$$
J,U,A,B \longmapsto W,R \longmapsto E,H,C,P,N .
$$
The read first displays the located interval source, the upper-bound ledger, the lower-approximation ledger, and the retained bisection or refinement row; it then opens finite StreamName windows, reads them through RegSeqRat, and only then consumes the terminal Real seal. The route exports no selected host supremum, quotient real equality, countable choice, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the carrier rows named in \autoref{def:located-interval-supremum-carrier}. A Real-facing supremum read has no access to the seal $E$ until the interval source $J$, upper-bound ledger $U$, lower-approximation ledger $A$, and bisection row $B$ have been displayed.

The finite readback route is fixed by those rows. The bisection and approximation ledgers determine the requested finite windows $W$, and the regular rational readback $R$ is attached to those same windows before the seal can be consumed.

Transport and replay do not create a new supremum source. The rows $H$ and $C$ move and replay only the displayed coordinates, while $P$ and $N$ record provenance and local naming for the same packet.

Thus every exported Real-facing observation factors through $J,U,A,B,W,R,E,H,C,P,N$. Since no coordinate of the packet carries a host supremum selector, quotient equality, choice, trichotomy, open-cover compactness, or ambient completeness, none of those principles is exported by the route.
\end{proof}

\falsifiablePrediction{Every $\LocatedIntervalSupremumUp$ Real-facing read factors through one located interval source row, one upper-bound ledger, one lower-approximation ledger, one bisection and refinement row, one StreamName window row, one RegSeqRat readback row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert.}

\independenceWitness{Nearest siblings: locatedsupremum, located-interval-bisection, bounded-complete-real-interval, dyadicratcore, streamname, regseqrat, and real. $\LocatedIntervalSupremumUp$ is not bijective to any listed sibling because it jointly carries interval source data, upper-bound exposure, lower-approximation cofinality, bisection-window exactness, readback, Real sealing, transport, replay, provenance, and local naming as one packet.}

\closureat{LocatedIntervalSupremumUp}{seedStr}

\begin{closurestatus}{\LocatedIntervalSupremumUp}
  \constructivestory{A $\LocatedIntervalSupremumUp$ packet is generated from a located interval source, an upper-bound ledger, a lower-approximation ledger, a bisection and refinement row, finite StreamName windows, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-interval-supremum-carrier}, \autoref{thm:located-interval-supremum-namecert-obligations}, and \autoref{thm:located-interval-supremum-real-seal-route} seed the finite interval-supremum route over located interval, bound, approximation, bisection, readback, Real seal, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim general $\RealUp$ completeness, selected host suprema, quotient real equality, countable choice, trichotomy, open-cover compactness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, upper-bound exposure, lower-approximation cofinality, bisection-window exactness, RegSeqRat handoff, Real seal routing, transport, replay, provenance, and local naming for BEDC.Derived.LocatedIntervalSupremumUp.}
\end{closurestatus}
