\chapter{A Concrete Naming Certificate for $\OrdinalAnalysisUp$}
\label{ch:concrete-instances-ordinal-analysis-namecert}
\origin{human}

Following Gentzen and proof-theoretic ordinal analysis, the $\OrdinalAnalysisUp$ packet records the finite ordinal-notation and descent-budget surface that a proof-normalization consumer may read before it reaches the MetaCIC normalization frontier. It sits beside the decidability boundary of \autoref{ch:concrete-instances-metacicdecidableboundary-namecert}, the normalization frontier of \autoref{ch:concrete-instances-metacicnormalizationfrontier-namecert}, the natural-deduction proof-tree surface of \autoref{ch:concrete-instances-natural-deduction-namecert}, the first-order syntax carrier of \autoref{ch:concrete-instances-firstorder-namecert}, and the lambda-calculus proof-term boundary of \autoref{ch:concrete-instances-lambdacalc-namecert}. The packet names only notation, descent, trace, consumer, refusal, transport, replay, provenance, and local naming rows; it does not assert global normalization, a host proof ordinal, or an unrestricted consistency theorem.

\begin{definition}[Ordinal analysis carrier]
\label{def:ordinal-analysis-carrier}
An $\OrdinalAnalysisUp$ carrier is a finite $\BHist$ packet
$$
O=(A,B,C,U,L,H,R,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the ordinal-notation row, read as a finite notation code and comparison window rather than as a completed host ordinal.
\item $B$ is the descent-budget row, recording the finite measure used by a cut-elimination or normalization trace.
\item $C$ is the cut-elimination trace row, displaying the local reduction or cut-reduction steps whose budget is being consumed.
\item $U$ is the normalization-consumer row, naming the $\MetaCICNormalizationFrontierUp$, $\NaturalDeductionUp$, $\FirstOrderUp$, or $\LambdaCalcUp$ reader that may inspect the trace.
\item $L$ is the refusal ledger, recording absent global-normalization, host-ordinal, subject-reduction, confluence, and consistency coordinates.
\item $H$ records componentwise $\hsame$ transport for the notation, budget, trace, consumer, refusal, replay, provenance, and local naming rows.
\item $R$ records displayed $\Cont$ replay from ordinal notation and descent budget through the trace into the named consumer boundary.
\item $P$ is the $\Pkg$ provenance over $\OrdinalAnalysisUp$, $\MetaCICDecidableBoundaryUp$, $\MetaCICNormalizationFrontierUp$, $\NaturalDeductionUp$, $\FirstOrderUp$, $\LambdaCalcUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\OrdinalAnalysisUp}$ row.
\end{enumerate}
The carrier has no coordinate for an ambient well-order theorem, a completed proof ordinal, a host consistency proof, a blanket cut-elimination theorem, or global MetaCIC normalization.
\end{definition}

\begin{theorem}[Ordinal analysis NameCert obligations]
\label{thm:ordinal-analysis-namecert-obligations}
For every accepted $\OrdinalAnalysisUp$ carrier $O=(A,B,C,U,L,H,R,P,N)$, the local $\NameCert_{\OrdinalAnalysisUp}$ surface consists exactly of carrier admission for ordinal notation, descent budget, cut-elimination trace, normalization consumer, refusal ledger, transport, replay, provenance, and local naming; descent exactness requiring the trace row $C$ to consume only the displayed budget $B$ over the notation row $A$; consumer compatibility requiring every $\MetaCICNormalizationFrontierUp$, $\MetaCICDecidableBoundaryUp$, $\NaturalDeductionUp$, $\FirstOrderUp$, or $\LambdaCalcUp$ read to pass through $U$; and nonescape excluding host proof ordinals, global normalization, unchecked subject reduction, unchecked confluence, and external consistency claims.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:ordinal-analysis-carrier}. The displayed rows are exactly $A,B,C,U,L,H,R,P,N$, so the local certificate has no source outside this finite packet.

Descent exactness is read from $A,B,C$. The notation row supplies the comparison window, the budget row supplies the finite descent measure, and the trace row records only the reduction steps charged to that budget.

Consumer compatibility is read from $U,R,P,N$. Replay and provenance make the named MetaCIC, natural-deduction, first-order, and lambda-calculus readers consume the displayed route rather than a detached host proof.

Finally, the refusal ledger $L$ and the absence of further carrier coordinates exclude ambient proof ordinals, unrestricted normalization, subject reduction, confluence, and consistency claims. Thus the listed rows exhaust the NameCert obligations.
\end{proof}

\begin{theorem}[Cut-elimination budget boundary]
\label{thm:ordinal-analysis-cut-elimination-budget}
Every cut-elimination or normalization-facing read of an accepted $\OrdinalAnalysisUp$ carrier must expose the route
$$
A,B,C,U,L,H,R,P,N
$$
before it can be consumed by $\MetaCICNormalizationFrontierUp$, $\MetaCICDecidableBoundaryUp$, $\NaturalDeductionUp$, $\FirstOrderUp$, or $\LambdaCalcUp$. The budget row $B$ is a finite BEDC descent ledger attached to the notation row $A$ and trace row $C$; it is not a host proof ordinal and does not by itself close global normalization.
\end{theorem}
\begin{proof}
Read the analytic rows first. The notation row $A$ and descent-budget row $B$ precede the trace row $C$, so any cut-elimination consumer receives a finite charged trace rather than an unbounded ordinal argument.

Next read the consumer row $U$. It records which sibling boundary is allowed to inspect the trace: the MetaCIC decidability and normalization frontiers, the natural-deduction proof-tree packet, the first-order syntax carrier, or the lambda-calculus proof-term carrier.

The support rows $H,R,P,N$ transport, replay, source, and name the same route. Since $L$ records the refused readings and no carrier coordinate supplies a completed proof ordinal or global normalization theorem, the budget remains a boundary object for downstream consumers.
\end{proof}

\falsifiablePrediction{A packet claiming $\OrdinalAnalysisUp$ acceptance while omitting ordinal notation, descent budget, cut-elimination trace, normalization consumer, refusal ledger, transport, replay, provenance, or local NameCert rows fails local certification before any MetaCIC normalization-frontier read can begin.}

\independenceWitness{metacicnormalizationfrontier, metacicdecidableboundary, natural-deduction, firstorder, lambdacalc: $\OrdinalAnalysisUp$ is not bijective to any listed sibling because it carries an ordinal-notation row, a descent-budget row, a cut-elimination trace row, a named normalization-consumer row, and a refusal ledger as one finite packet. The MetaCIC frontier chapters carry bounded normalization and decidability surfaces without a proof-theoretic descent ledger; NaturalDeductionUp carries proof trees without ordinal notation; FirstOrderUp carries syntax and deduction endpoints; LambdaCalcUp carries term reduction rows without the displayed ordinal-analysis budget.}

\closureat{OrdinalAnalysisUp}{seedStr}

\begin{closurestatus}{\OrdinalAnalysisUp}
  \constructivestory{An $\OrdinalAnalysisUp$ packet is generated from ordinal notation, descent budget, cut-elimination trace, normalization-consumer, refusal-ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:ordinal-analysis-carrier}, \autoref{thm:ordinal-analysis-namecert-obligations}, and \autoref{thm:ordinal-analysis-cut-elimination-budget} seed the finite proof-theoretic descent route consumed by MetaCIC and proof-calculus boundaries.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, global normalization, host proof ordinals, unrestricted cut elimination, subject reduction, confluence, or consistency for $\OrdinalAnalysisUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, descent-budget exactness, cut-elimination trace replay, normalization-consumer compatibility, refusal-ledger nonescape, transport, replay, provenance, and local naming for BEDC.Derived.OrdinalAnalysisUp.}
\end{closurestatus}
