\chapter{A Concrete Naming Certificate for $\CountablyBasedUniformityUp$}
\label{ch:concrete-instances-countably-based-uniformity-namecert}
\origin{human}

Following Bourbaki and Kelley, the $\CountablyBasedUniformityUp$ packet records the standard countable-base interface for a uniform space as finite BEDC naming data. It sits after the entourage discipline of \autoref{ch:concrete-instances-uniformspace-namecert}, the Cauchy-filter consumer of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet gives completion consumers a countable basis route, not an arbitrary open-cover uniformity, quotient equality, countable-choice selector, or ambient completeness principle.

\begin{definition}[CountablyBasedUniformity carrier]
\label{def:countably-based-uniformity-carrier}
A $\CountablyBasedUniformityUp$ carrier is a finite $\BHist$ packet
$$
U=(E,F,S,Q,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $E$ is the $\UniformSpaceUp$ entourage row whose requests are read only through the displayed countable basis.
\item $F$ is the $\CauchyFilterUp$ consumer row that receives Cauchy data from the basis rather than from an arbitrary open-cover surface.
\item $S$ is the $\StreamNameUp$ finite-window row indexing the displayed countable basis requests.
\item $Q$ is the $\RegSeqRatUp$ regular rational readback row attached to those windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger controlling finite refinements between basis elements.
\item $R$ is the downstream $\RealUp$ seal row available only after $E,F,S,Q,D$ have been replayed.
\item $H$ records componentwise $\hsame$ transport for the uniform, filter, window, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
E,F \longmapsto S,Q,D \longmapsto R .
$$
\item $P$ is the $\Pkg$ provenance over $\CountablyBasedUniformityUp$, $\UniformSpaceUp$, $\CauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\CountablyBasedUniformityUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $E,F,S,Q,D,R,H,C,P,N$. It has no coordinate for arbitrary open-cover uniformity, quotient equality of uniform spaces, countable choice, selected Cauchy-filter limits, host Real equality, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[CountablyBasedUniformity NameCert obligations]
\label{thm:countably-based-uniformity-namecert-obligations}
For every accepted $\CountablyBasedUniformityUp$ carrier
$$
U=(E,F,S,Q,D,R,H,C,P,N),
$$
the local $\NameCert_{\CountablyBasedUniformityUp}$ surface consists exactly of carrier admission for the displayed rows, countable basis coverage for the $\UniformSpaceUp$ requests, finite refinement stability through the $\DyadicRatCoreUp$ ledger, $\CauchyFilterUp$ handoff through the generated basis, completion-consumer compatibility through the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ route, and ledger nonescape from arbitrary open-cover uniformity, quotient equality, countable choice, selected limits, host Real equality, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:countably-based-uniformity-carrier}. The projection exposes exactly the uniform entourage row, Cauchy-filter consumer, stream-window basis index, regular rational readback, dyadic tolerance ledger, Real seal, and structural rows.

The countable-basis part is read through $E,S,Q,D$. The row $S$ displays the finite windows for the basis, $Q$ supplies the regular rational readback, and $D$ records the finite refinement relation between basis elements before any completion-facing consumer can inspect the seal.

The filter and completion handoff then uses $F$ and $R$. A Cauchy-filter request must pass through the generated basis before reaching the downstream Real seal, so the consumer receives a basis-indexed route rather than arbitrary open-cover data.

Finally $H,C,P,N$ transport, replay, source, and name the same finite packet. Since none of the excluded principles occurs as a carrier coordinate, no NameCert obligation can export quotient equality, countable choice, selected limits, host equality, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\CountablyBasedUniformityUp$ completion consumer that reaches a $\RealUp$ seal without displaying $\UniformSpaceUp$, $\CauchyFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row refutes the packet surface.}

\independenceWitness{uniformspace, cauchyfilter, streamname, regseqrat, dyadicratcore, real: no listed sibling is bijective to $\CountablyBasedUniformityUp$ because this packet binds countable basis coverage, finite refinement stability, Cauchy-filter handoff, completion-consumer compatibility, transport, replay, provenance, and local naming as one L10 route.}

\closureat{CountablyBasedUniformityUp}{seedStr}

\begin{closurestatus}{\CountablyBasedUniformityUp}
  \constructivestory{A $\CountablyBasedUniformityUp$ packet is generated from a UniformSpace entourage row, CauchyFilter consumer row, StreamName finite-window basis row, RegSeqRat readback row, DyadicRatCore finite-refinement ledger, RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:countably-based-uniformity-carrier} and \autoref{thm:countably-based-uniformity-namecert-obligations} seed the countable-basis uniformity interface for Cauchy-filter and completion-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary open-cover uniformity, quotient equality, selected limits, countable choice, host Real equality, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, countable basis coverage, finite refinement stability, Cauchy-filter handoff, completion-consumer compatibility, transport, replay, provenance, local naming, and ledger nonescape for BEDC.Derived.CountablyBasedUniformityUp.}
\end{closurestatus}
