\chapter{A Concrete Naming Certificate for $\RegularCauchySaturationUp$}
\label{ch:concrete-instances-regular-cauchy-saturation-namecert}
\origin{ai}

The $\RegularCauchySaturationUp$ packet realizes the real-completion vision route of \autoref{ch:visions-real-completeness} and \autoref{sec:real-completeness-regular-cauchy} as a finite tail-budget closure surface. It binds the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window naming discipline of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal seal of \autoref{ch:concrete-instances-real-namecert}, and the equality boundary of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}. The packet names a saturation route for finite tail windows; it does not assert full real completeness, selected limits, quotient representatives, countable choice, or a global metric completion theorem.

\begin{definition}[Regular Cauchy saturation carrier]
\label{def:regular-cauchy-saturation-carrier}
A $\RegularCauchySaturationUp$ carrier is a finite $\BHist$ packet
$$
S=(W,R,D,E,Q,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $W$ is the $\StreamNameUp$ finite tail-window row, naming the inspected regular Cauchy stages and the requested precision window.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger, recording the requested rational radius, tail comparison budget, and diagonal readback arithmetic.
\item $E$ is the terminal $\RealUp$ seal row reached only after $W,R,D$ have been displayed.
\item $Q$ is the $\CauchyEquivalenceSetoidUp$ boundary row, recording equality only through the displayed tail-window and tolerance route.
\item $H$ records componentwise $\hsame$ transport for the window, readback, tolerance, real-seal, setoid-boundary, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay through
$$
W,R,D,Q \longmapsto E \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\RegularCauchySaturationUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyEquivalenceSetoidUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RegularCauchySaturationUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $W,R,D,E,Q,H,C,P,N$. It has no coordinate for a selected limit, quotient stream representative, countable-choice schedule, ambient completeness theorem, or host equality of real names.
\end{definition}

\begin{theorem}[Regular Cauchy saturation NameCert obligations]
\label{thm:regular-cauchy-saturation-namecert-obligations}
For every accepted $\RegularCauchySaturationUp$ carrier $S=(W,R,D,E,Q,H,C,P,N)$, the local $\NameCert_{\RegularCauchySaturationUp}$ surface consists exactly of finite tail-window admission through $W$, regular-rational readback through $R$, dyadic tolerance accounting through $D$, terminal real-seal exposure through $E$, Cauchy-equivalence boundary routing through $Q$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$. No local obligation may read full $\RealUp$ completeness, a selected limit representative, quotient stream equality, countable choice, metric-completion universality, or host real equality.
\end{theorem}
\begin{proof}
Project the accepted carrier. The completion-facing data are exactly the tail-window row $W$, regular-rational readback row $R$, dyadic tolerance row $D$, terminal real-seal row $E$, and setoid-boundary row $Q$.

The finite tail-window row comes first. It fixes the stages and precision request before the regular rational readback and dyadic comparison can be inspected.

The equality boundary is then only a displayed Cauchy-equivalence route over the same rows. Componentwise transport, continuation replay, provenance, and local naming preserve this finite surface and do not add a selected limit, quotient representative, choice schedule, universal completion object, or ambient completeness theorem.
\end{proof}

\falsifiablePrediction{A $\RegularCauchySaturationUp$ consumer that reaches a terminal $\RealUp$ seal without the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\CauchyEquivalenceSetoidUp$ rows refutes the packet surface.}

\independenceWitness{streamname, regseqrat, dyadicratcore, real, cauchy-equivalence-setoid: none is bijective to $\RegularCauchySaturationUp$ because this packet jointly carries finite tail windows, regular-rational readback, dyadic tolerance, terminal Real seal, Cauchy-equivalence boundary, transport, replay, provenance, and local naming rows.}

The Lean TasteGate follow-up for $\RegularCauchySaturationUp$ must include explicit $\mathsf{Nontrivial}\ \RegularCauchySaturationUp$ and $\mathsf{FieldFaithful}\ \RegularCauchySaturationUp$ instances, with field faithfulness preserving the order $W,R,D,E,Q,H,C,P,N$.

\closureat{RegularCauchySaturationUp}{seedStr}

\begin{closurestatus}{\RegularCauchySaturationUp}
  \constructivestory{A $\RegularCauchySaturationUp$ packet is generated from StreamName finite tail windows, RegSeqRat readback, DyadicRatCore tolerance accounting, a RealUp seal row, a CauchyEquivalenceSetoid boundary row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-saturation-carrier} and \autoref{thm:regular-cauchy-saturation-namecert-obligations} seed the finite tail-budget route from regular Cauchy windows to the terminal Real seal and Cauchy-equivalence boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim full real completeness, selected limit representatives, quotient stream equality, countable choice, metric-completion universality, host real equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked tail-window admission, regular-rational readback, dyadic tolerance accounting, terminal Real seal routing, Cauchy-equivalence boundary exposure, transport, replay, provenance, and local naming for BEDC.Derived.RegularCauchySaturationUp.}
\end{closurestatus}
