\chapter{A Concrete Naming Certificate for $\UnifiedEpistemicObjectUp$}
\label{ch:concrete-instances-unified-epistemic-object-namecert}
\origin{ai}

The $\UnifiedEpistemicObjectUp$ packet realizes the unified closure pattern of \autoref{sec:visions-philosophy-unified-theory-closure} as finite NameCert data. It gathers generated material, classifier surface, certificate rows, ledger accounting, theorem-DNA roles, hardening profile, and scope seal into one auditable object. The packet sits beside the classifier-novelty ledger of \autoref{ch:concrete-instances-classifier-novelty-ledger-namecert}, the scoped explanation ledger of \autoref{ch:concrete-instances-scoped-explanation-ledger-namecert}, and the theorem-DNA score surface of \autoref{ch:concrete-instances-theorem-dna-score-namecert}; it does not claim positive discovery without a later TasteGate witness.

\begin{definition}[Unified epistemic object carrier]
\label{def:unified-epistemic-object-carrier}
A $\UnifiedEpistemicObjectUp$ carrier is a finite $\BHist$ packet
$$
U=(G,R,C,N,L,D,F,O,T,H,K,P,M)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the generated-material row, covering observed material, proof traces, learned traces, theorem candidates, or intervention records.
\item $R$ is the record row that fixes the local source scope and replayable material boundary.
\item $C$ is the classifier row for the stated source scope.
\item $N$ is the certificate row, carrying the local NameCert or Tensor NameCert data for $C$.
\item $L$ is the ledger row recording residue from identification, compression, projection, thresholding, semantic assignment, verification, intervention, and scope refusal.
\item $D$ is the theorem-DNA row recording role-complete loci for the object.
\item $F$ is the hardening-profile row, recording which loci are hardened, which remain ledger-only, and which backend boundary is being used.
\item $O$ is the scope-seal row, naming source scope, target scope, claim kind, not-claimed boundary, and closure route.
\item $T$ is the classifier-nonescape row: every accepted classifier read must pass through $G,R,C,N,L,D,F,O$.
\item $H$ records componentwise $\hsame$ transport for all rows.
\item $K$ records displayed $\Cont$ replay from generated material through classifier, certificate, ledger, DNA, hardening, and seal rows.
\item $P$ is the $\Pkg$ provenance over $\UnifiedEpistemicObjectUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $M$ is the local $\NameCert_{\UnifiedEpistemicObjectUp}$ row.
\end{enumerate}
The accepted carrier has no coordinate for a bare classifier claim, an unledgered hardening claim, a positive-discovery verdict, a Nontrivial instance, a FieldFaithful instance, or a TasteGate result.
\end{definition}

\begin{theorem}[Unified epistemic object NameCert obligations]
\label{thm:unified-epistemic-object-namecert-obligations}
For every accepted $\UnifiedEpistemicObjectUp$ carrier $U=(G,R,C,N,L,D,F,O,T,H,K,P,M)$, the local $\NameCert_{\UnifiedEpistemicObjectUp}$ obligations are exhausted by generated material, record scope, classifier, certificate, ledger, theorem-DNA, hardening-profile, scope-seal, classifier-nonescape, transport, replay, provenance, and local naming rows. In particular, the carrier does not certify positive discovery, Nontriviality, or FieldFaithfulness merely by packaging the rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:unified-epistemic-object-carrier}. The material and record rows $G,R$ determine the source boundary, and the classifier row $C$ is readable only relative to that boundary.

Read the certificate and ledger rows next. The row $N$ records the certificate surface for $C$, while $L$ records the residue that prevents classifier assertions from escaping their declared accounting surface.

The theorem-DNA, hardening, and seal rows then place the object in its role, backend, and scope boundaries. The nonescape row $T$ says that classifier reads must pass through all of these rows before any public claim can be exported.

The remaining structural rows $H,K,P,M$ transport, replay, account for provenance, and name the same packet. None of them supplies a TasteGate verdict, Nontrivial instance, FieldFaithful instance, or positive-discovery result, so those obligations remain outside this carrier.
\end{proof}

\begin{theorem}[Unified epistemic object classifier nonescape]
\label{thm:unified-epistemic-object-classifier-nonescape}
Let $U=(G,R,C,N,L,D,F,O,T,H,K,P,M)$ be an accepted $\UnifiedEpistemicObjectUp$ carrier. Every classifier-facing read exported by $U$ factors through
$$
G,R \longmapsto C \longmapsto N,L,D,F,O \longmapsto T,H,K,P,M .
$$
Consequently a downstream consumer cannot read a bare classifier, unledgered verification claim, unsealed theorem-DNA packet, or positive-discovery verdict from the carrier.
\end{theorem}
\begin{proof}
Start with the generated-material and record rows. They fix the local source scope before a classifier can be read.

Apply the classifier and certificate rows. The classifier row $C$ is named by $N$, and the ledger row $L$ records residue from the relevant source and semantic operations.

Use the theorem-DNA, hardening-profile, and scope-seal rows. They bind role completeness, backend exposure, and public claim scope before any classifier-facing output may leave the packet.

Finally apply the classifier-nonescape row $T$ and replay through $H,K,P,M$. Since the carrier has no row for a bare classifier, unledgered hardening claim, unsealed DNA packet, or TasteGate verdict, none of those objects can be exported by an accepted read.
\end{proof}

\falsifiablePrediction{A downstream classifier report that reads a $\UnifiedEpistemicObjectUp$ classifier without generated material, record scope, certificate, ledger, theorem-DNA, hardening profile, and scope seal refutes the classifier-nonescape row.}

\independenceWitness{classifier-novelty-ledger, scoped-explanation-ledger, theorem-dna-score, hard-certificate-layer, audit-axis-separation: none is bijective to $\UnifiedEpistemicObjectUp$ because each sibling contributes only part of the generated-material, classifier, certificate, ledger, theorem-DNA, hardening-profile, scope-seal, nonescape, transport, replay, provenance, and local naming packet.}

\closureat{UnifiedEpistemicObjectUp}{seedStr}

\begin{closurestatus}{\UnifiedEpistemicObjectUp}
  \constructivestory{A $\UnifiedEpistemicObjectUp$ packet is generated from material, record, classifier, certificate, ledger, theorem-DNA, hardening-profile, scope-seal, classifier-nonescape, transport, replay, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:unified-epistemic-object-carrier}, \autoref{thm:unified-epistemic-object-namecert-obligations}, and \autoref{thm:unified-epistemic-object-classifier-nonescape} seed the finite unified epistemic object packet without a discovery verdict.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close positive discovery, Nontriviality, FieldFaithfulness, TasteGate acceptance, Lean verification, bridge checking, or any classifier shift beyond the displayed carrier rows.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier nonescape, ledger closure, theorem-DNA compatibility, hardening-profile accounting, scope-seal replay, and later TasteGate work for Nontrivial and FieldFaithful instances.}
\end{closurestatus}
