\chapter{A Concrete Naming Certificate for $\RegularCauchyRealReflectionUp$}
\label{ch:concrete-instances-regular-cauchy-real-reflection-namecert}
\origin{human}

Following Bishop and Bridges on constructive real numbers, the $\RegularCauchyRealReflectionUp$ packet names the finite route by which a regular rational Cauchy sequence can be read as a Real-facing seal without importing quotient stream equality or host real equality. It sits after the regular rational source of \autoref{ch:concrete-instances-regseqrat-namecert}, the finite-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the quotient-discipline boundary of \autoref{ch:concrete-instances-cauchy-equivalence-setoid-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a concrete L10 reflection route from classifier data to the public Real seal; it is not an assertion of ambient completeness, a selected representative theorem, or a host-limit construction.

\begin{definition}[RegularCauchyRealReflection carrier]
\label{def:regular-cauchy-real-reflection-carrier}
A $\RegularCauchyRealReflectionUp$ carrier is a finite $\BHist$ packet
$$
M=(G,S,E,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $G$ is the $\RegSeqRatUp$ source row naming the regular rational Cauchy sequence whose Real-facing reflection is being inspected.
\item $S$ is the $\StreamNameUp$ finite-window row exposing the inspected prefixes, tail windows, and replay schedule for $G$.
\item $E$ is the $\CauchyEquivalenceSetoidUp$ classifier row recording exactly the displayed equivalence comparisons admitted for the regular sequence route.
\item $D$ is the $\DyadicRatCoreUp$ tolerance-window row, with dyadic budgets aligned to the regular-Cauchy classifier comparisons named by $E$.
\item $R$ is the terminal $\RealUp$ seal row. It is visible only after $G,S,E,D$ display the regular source, finite windows, admissible Cauchy-equivalence comparisons, and dyadic tolerance windows.
\item $H$ records componentwise $\hsame$ transport for the regular source, stream windows, equivalence classifier, dyadic tolerance windows, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a Real-facing reflection request through $G,S,E,D,R,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\RegularCauchyRealReflectionUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\CauchyEquivalenceSetoidUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RegularCauchyRealReflectionUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $G,S,E,D,R,H,C,P,N$. It has no coordinate for quotient stream equality, a selected representative of the equivalence class, a host real limit, ambient real equality, countable choice, or an external completeness theorem.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyRealReflectionUp.RegularCauchyRealReflectionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[RegularCauchyRealReflection NameCert obligations]
\label{thm:regular-cauchy-real-reflection-namecert-obligations}
For every accepted $\RegularCauchyRealReflectionUp$ carrier
$$
M=(G,S,E,D,R,H,C,P,N),
$$
the local $\NameCert_{\RegularCauchyRealReflectionUp}$ surface consists exactly of carrier admission for $M$, regular-Cauchy classifier exposure through $G$ and $E$, dyadic tolerance-window exactness through $D$, terminal $\RealUp$ seal reflection through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$. The certificate is stable under replay of the same displayed stream windows and tolerance budgets, and it never exports quotient stream equality or host real equality.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-cauchy-real-reflection-carrier}. The accepted source is the regular rational row $G$, and the only observable finite data for that source are the windows named by $S$.

The classifier rows are explicit. The Cauchy-equivalence row $E$ records the admissible comparisons, while the dyadic tolerance row $D$ records the exact tolerance windows used by those comparisons. No extra equality predicate is available outside these rows.

The Real-facing row $R$ is therefore terminal for the displayed route. It can be read only after $G,S,E,D$ have exposed the regular source, finite windows, classifier comparisons, and dyadic tolerances.

The remaining rows do not add analytic content. They transport the same data by $H$, replay the same route by $C$, record source accountability by $P$, and bind the local name by $N$. Since no row stores quotient stream equality, a selected representative, a host real limit, ambient real equality, countable choice, or external completeness, the listed rows exhaust the NameCert obligations.
\end{proof}

\falsifiablePrediction{Every accepted $\RegularCauchyRealReflectionUp$ reflection factors through one RegSeqRatUp source row, one StreamNameUp finite-window row, one CauchyEquivalenceSetoidUp classifier row, one DyadicRatCoreUp tolerance-window row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{regseqrat, streamname, cauchy-equivalence-setoid, dyadicratcore, real: $\RegularCauchyRealReflectionUp$ is not bijective to any listed sibling because it packages the regular-Cauchy classifier, finite windows, dyadic tolerance windows, terminal Real seal, transport, replay, provenance, and local NameCert as one reflection certificate.}

\closureat{RegularCauchyRealReflectionUp}{seedStr}

\begin{closurestatus}{\RegularCauchyRealReflectionUp}
  \constructivestory{A $\RegularCauchyRealReflectionUp$ packet is generated from a RegSeqRatUp source row, StreamNameUp finite windows, a CauchyEquivalenceSetoidUp classifier row, DyadicRatCoreUp tolerance windows, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-cauchy-real-reflection-carrier} and \autoref{thm:regular-cauchy-real-reflection-namecert-obligations} seed the finite reflection route from regular rational Cauchy classifier data to the Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient Real completeness, quotient equality, selected representatives, host limits, host real equality, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, regular-Cauchy classifier exposure, dyadic tolerance-window exactness, Real seal reflection, transport, replay, provenance, local naming, and nonescape for BEDC.Derived.RegularCauchyRealReflectionUp.}
\end{closurestatus}
