\chapter{A Concrete Naming Certificate for $\FiniteVolumeUp$}
\label{ch:concrete-instances-finite-volume-namecert}
\origin{human}

Following LeVeque and Eymard--Gallouet--Herbin, the $\FiniteVolumeUp$ packet records conservative finite-mesh balance as BEDC-visible ledger data. It sits over the mesh cells of \autoref{ch:concrete-instances-finite-partition-mesh-namecert}, the gauge and sum interfaces of \autoref{ch:concrete-instances-riemann-sum-gauge-namecert} and \autoref{ch:concrete-instances-darboux-sum-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the PDE relation surface of \autoref{ch:concrete-instances-pde-namecert}. The packet names the finite conservation rows inspected by numerical PDE consumers; it does not import a host solution, mesh-limit convergence theorem, weak formulation quotient, solver trace, or ambient $\RealUp$ completeness.

\begin{definition}[Finite-volume carrier]
\label{def:finite-volume-carrier}
A $\FiniteVolumeUp$ carrier is a finite $\BHist$ packet
$$
V=(M,F,X,B,S,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the $\FinitePartitionMeshUp$ cell-mesh row, carrying finitely many control volumes with their displayed incidence names.
\item $F$ is the face-incidence row, pairing each interior face with its two adjacent cells and each boundary face with its boundary tag.
\item $X$ is the flux ledger, storing one oriented numerical flux entry for each displayed face incidence and the local stencil rows used to read it.
\item $B$ is the boundary ledger, storing boundary flux, source, or trace data only along faces marked boundary by $F$.
\item $S$ is the residual and conservation-balance row, recording for each cell the sum of incoming and outgoing face flux entries together with source and residual rows.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the cellwise flux, source, residual, and balance windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row used to compare paired face contributions and displayed residual budgets.
\item $E$ is the terminal $\RealUp$ seal row reached only after $M,F,X,B,S,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the mesh, incidence, flux, boundary, residual, regular readback, dyadic tolerance, Real seal, replay, provenance, and local naming rows.
\item $C$ is the displayed $\Cont$ replay from a finite cell-balance request through $M,F,X,B,S,R,D,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\FiniteVolumeUp$, $\FinitePartitionMeshUp$, $\RiemannSumGaugeUp$, $\DarbouxSumUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\PdeUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteVolumeUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for a host PDE solution, unrestricted mesh refinement limit, quotient weak solution, selected trace, hidden solver state, or ambient real completeness theorem.
\end{definition}

\begin{theorem}[Finite-volume conservation balance]
\label{thm:finite-volume-conservation-balance}
For every accepted $\FiniteVolumeUp$ carrier
$$
V=(M,F,X,B,S,R,D,E,H,C,P,N),
$$
the aggregate conservation read over any displayed finite set of cells cancels every interior face flux that is paired by the incidence row $F$. The visible aggregate balance consists only of boundary-ledger contributions from $B$, displayed source rows, residual rows from $S$, and the downstream $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ seal data. It does not assert a host PDE solution, unrestricted convergence of a mesh family, selected weak trace, quotient equality of approximate solutions, or ambient completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-volume-carrier}. The row $F$ is the only source of face incidence, so every interior face visible to the packet appears with exactly the two adjacent cell orientations recorded by that row.

Read the oriented flux ledger $X$ through the same incidence data. In a cellwise aggregate, the contribution of an interior face is inspected once from each adjacent cell with opposite orientation, so those two displayed ledger entries cancel as a pair. Boundary faces have no second adjacent cell row, hence they remain visible through the boundary ledger $B$.

The residual and conservation row $S$ then records exactly what remains after the paired interior cancellations: boundary contributions, displayed source rows, and residual rows. The $\RegSeqRatUp$ readback $R$, $\DyadicRatCoreUp$ tolerance row $D$, and $\RealUp$ seal $E$ are downstream of this balance, while $H,C,P,N$ transport, replay, source, and name the same finite route. No excluded host solution, mesh-limit, quotient, trace, or completeness coordinate is present in the carrier.
\end{proof}

\closureat{FiniteVolumeUp}{seedStr}

\begin{closurestatus}{\FiniteVolumeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-volume-carrier} and \autoref{thm:finite-volume-conservation-balance} seed the conservative finite-volume packet over mesh cells, face incidence, flux ledgers, boundary rows, residual balances, RegSeqRat readback, dyadic tolerance, RealUp seals, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host PDE solutions, unrestricted mesh-limit convergence, quotient weak-solution equality, selected traces, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked mesh admission, face-incidence pairing, flux-ledger transport, boundary-ledger routing, residual-balance exactness, regular readback, dyadic tolerance, Real-seal admission, replay, provenance, and local naming for BEDC.Derived.FiniteVolumeUp.}
  \constructivestory{A $\FiniteVolumeUp$ packet is generated from a FinitePartitionMeshUp cell mesh, face incidence rows, oriented flux ledgers, boundary ledgers, residual conservation balances, RegSeqRat readback, DyadicRatCore tolerance, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
