\chapter{A Concrete Naming Certificate for $\CompactUniformCauchyModulusUp$}
\label{ch:concrete-instances-compact-uniform-cauchy-modulus-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\CompactUniformCauchyModulusUp$ packet records the finite compact-indexed modulus extraction by which a uniformly Cauchy family over a compact metric source supplies one shared tail schedule for Real and Completion consumers. It sits over the compact metric surface of \autoref{ch:concrete-instances-compactmetric-namecert}, the compact uniform Cauchy route of \autoref{ch:concrete-instances-compact-uniform-cauchy-namecert}, the Cauchy-modulus schedule of \autoref{ch:concrete-instances-cauchymodulus-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a NameCert carrier for a compact-indexed tail schedule; it is not an open-cover compactness theorem, not a selected limit construction, and not a host real equality principle.

\begin{definition}[Compact uniform Cauchy modulus carrier]\label{def:compact-uniform-cauchy-modulus-carrier}
A $\CompactUniformCauchyModulusUp$ carrier is a finite $\BHist$ packet
$$
U=(K,F,M,S,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the $\CompactMetricUp$ source row naming the compact metric index space whose finite cover data may be inspected.
\item $F$ is the $\UniformCauchyUp$ family row naming the uniformly Cauchy rational stream family over $K$.
\item $M$ is the $\CauchyModulusUp$ shared tail schedule chosen uniformly for the displayed compact source and family.
\item $S$ is the $\StreamNameUp$ finite-window row naming the stream positions read after the shared schedule in $M$.
\item $Q$ is the $\RegSeqRatUp$ regular rational readback row for the scheduled finite windows.
\item $E$ is the $\RealUp$ seal row available only after $K,F,M,S,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for compact source, family, modulus schedule, finite window, regular readback, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact-indexed precision request through $K,F,M,S,Q,E,H$.
\item $P$ is the $\Pkg$ provenance over $\CompactUniformCauchyModulusUp$, $\CompactMetricUp$, $\UniformCauchyUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactUniformCauchyModulusUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,F,M,S,Q,E,H,C,P,N$. It has no coordinate for a chosen compact cover, an extracted subnet, a selected limit, quotient stream equality, countable choice, host real equality, or ambient Real completeness.
\end{definition}

\begin{theorem}[Compact uniform Cauchy modulus NameCert obligations]\label{thm:compact-uniform-cauchy-modulus-namecert-obligations}
For every accepted $\CompactUniformCauchyModulusUp$ carrier $U=(K,F,M,S,Q,E,H,C,P,N)$, the local $\NameCert_{\CompactUniformCauchyModulusUp}$ surface consists exactly of carrier admission, compact metric source exposure, uniformly Cauchy family exposure, shared Cauchy-modulus extraction, finite stream-window exposure, regular rational readback, Real seal handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every Real or Completion consumer must read the displayed route
$$
K,F \longmapsto M \longmapsto S,Q \longmapsto E \longmapsto H,C,P,N
$$
before using a compact-indexed uniform tail schedule.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-uniform-cauchy-modulus-carrier}. The compact source row $K$ and the uniformly Cauchy family row $F$ are the only analytic inputs to the shared schedule.

Read $M$ next. The Cauchy-modulus row records one displayed tail schedule for the whole compact-indexed family, so a consumer cannot replace it by pointwise schedules detached from $K$ and $F$.

The finite stream-window row $S$ and the regular rational readback row $Q$ then expose the scheduled finite observations. The Real seal $E$ and structural rows $H,C,P,N$ transport, replay, source, and name the same route. Since selected limits, quotient stream equality, countable choice, host real equality, chosen compact covers, and ambient Real completeness are absent from the carrier, none of those data can occur in the local NameCert surface.
\end{proof}

\begin{theorem}[Compact finite-net tail extraction]\label{thm:compact-uniform-cauchy-modulus-finite-net-tail}
Let $U=(K,F,M,S,Q,E,H,C,P,N)$ be an accepted $\CompactUniformCauchyModulusUp$ carrier. Any finite-net or Real-and-Completion consumer that asks for a compact-indexed uniform tail must read $K,F,M,S,Q,E,H,C,P,N$ in the displayed order. The exported tail is therefore a finite $\StreamNameUp$ window and $\RegSeqRatUp$ readback governed by one shared $\CauchyModulusUp$ row over the $\CompactMetricUp$ source, not a pointwise family of radii, selected subnet, host limit, quotient stream, countable-choice schedule, or ambient compactness theorem.
\end{theorem}
\begin{proof}
Begin with the NameCert obligation theorem \autoref{thm:compact-uniform-cauchy-modulus-namecert-obligations}. It fixes the compact source, uniformly Cauchy family, shared schedule, finite window, rational readback, and Real seal as the whole public route.

A finite-net-facing consumer can inspect the compact source only through $K$ and the family only through $F$. The shared schedule $M$ must be read before any finite window $S$ or readback row $Q$ is available, so the tail cannot be assembled from detached pointwise radius schedules.

For a Real-and-Completion consumer, the seal row $E$ is reached only after the same finite route has been displayed. The replay and provenance rows preserve that route and add no selected subnet, host limit, quotient stream, countable-choice schedule, or ambient compactness theorem.
\end{proof}

\falsifiablePrediction{Every accepted $\CompactUniformCauchyModulusUp$ Real or Completion consumer factors through one $\CompactMetricUp$ source row, one $\UniformCauchyUp$ family row, one shared $\CauchyModulusUp$ schedule, one $\StreamNameUp$ finite-window row, one $\RegSeqRatUp$ readback row, one $\RealUp$ seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ before it may use a compact-indexed uniform tail.}

\independenceWitness{compactmetric, uniformcauchy, cauchymodulus, streamname, regseqrat, real: $\CompactUniformCauchyModulusUp$ is not bijective to any listed sibling because the siblings separately supply compact sources, uniformly Cauchy families, modulus schedules, finite stream windows, rational readback, and terminal Real sealing, while this packet binds them to one compact-indexed uniform tail schedule.}

\closureat{CompactUniformCauchyModulusUp}{seedStr}

\begin{closurestatus}{\CompactUniformCauchyModulusUp}
  \constructivestory{A $\CompactUniformCauchyModulusUp$ packet is generated from a CompactMetric source row, a UniformCauchy family row, a shared CauchyModulus schedule, a StreamName finite-window row, a RegSeqRat readback row, a Real seal handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-cauchy-modulus-carrier}, \autoref{thm:compact-uniform-cauchy-modulus-namecert-obligations}, and \autoref{thm:compact-uniform-cauchy-modulus-finite-net-tail} seed the compact-indexed uniform Cauchy modulus interface for the L10 Real and Completion route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected limits, quotient stream equality, countable choice, host real equality, Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact-source exposure, uniformly Cauchy family exposure, shared schedule exactness, finite-window readback, Real seal handoff, structural transport, provenance non-escape, and local NameCert exactness for BEDC.Derived.CompactUniformCauchyModulusUp.}
\end{closurestatus}
