\chapter{A Concrete Naming Certificate for $\BrouwerianCounterexampleUp$}
\label{ch:concrete-instances-brouwerian-counterexample-namecert}
\origin{human}

Following Brouwer, Troelstra--van Dalen, and Bridges--Richman on constructive counterexamples, the $\BrouwerianCounterexampleUp$ packet records a finite refusal surface for off-table L10 readings. It sits beside the finite observation route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the Specker obstruction boundary of \autoref{ch:concrete-instances-specker-sequence-boundary-namecert}. The packet makes the refusal of trichotomy, selected limits, quotient real equality, and ambient $\RealUp$ completeness inspectable as NameCert data rather than as an implicit metatheoretic convention.

\begin{definition}[Brouwerian counterexample carrier]\label{def:brouwerian-counterexample-carrier}
A $\BrouwerianCounterexampleUp$ carrier is a finite $\BHist$ packet
$$
B=(Q,A,S,R,E,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the tested L10 claim row, naming the proposed off-table reading such as trichotomy, selected limit extraction, quotient real equality, or ambient $\RealUp$ completeness.
\item $A$ is the finite counterexample source row, carrying the Brouwerian choice-sequence, bar, or Specker-style obstruction data used to test $Q$.
\item $S$ is the $\StreamNameUp$ window row through which the source is inspected by a downstream Real or Completion consumer.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the displayed windows in $S$.
\item $E$ is the $\RealUp$ readback boundary available only after the source, window, regular-rational, and refusal rows have been displayed.
\item $L$ is the refusal ledger recording which tested reading in $Q$ is not exported by the packet and which finite counterexample source row $A$ witnesses the refusal.
\item $H$ records componentwise $\hsame$ transport for the tested claim, counterexample source, stream window, regular readback, Real boundary, refusal ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the tested claim through the counterexample source, then through stream windows, regular readback, refusal ledger, and the terminal readback boundary.
\item $P$ is the $\Pkg$ provenance over $\BrouwerianCounterexampleUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\SpeckerSequenceBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BrouwerianCounterexampleUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $Q,A,S,R,E,L,H,C,P,N$. It has no coordinate for a completed host counterexample object, an omniscience principle, real trichotomy, quotient real equality, selected limits, countable choice, or ambient Real completeness.
\end{definition}

\begin{theorem}[Brouwerian counterexample NameCert obligations]\label{thm:brouwerian-counterexample-namecert-obligations}
For every accepted $\BrouwerianCounterexampleUp$ carrier $B=(Q,A,S,R,E,L,H,C,P,N)$, the local $\NameCert_{\BrouwerianCounterexampleUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the tested L10 claim, finite counterexample source, StreamName windows, RegSeqRat readback, Real boundary, refusal ledger, transport, replay, provenance, and local naming rows;
\item source exactness, requiring the row $A$ to be the only counterexample source used when the tested claim row $Q$ is evaluated;
\item windowed readback, requiring every Real or Completion-facing read to open $S$ and $R$ before consulting the Real boundary $E$;
\item refusal-ledger exactness, requiring the ledger $L$ to bind each refused reading to the displayed source and readback rows rather than to an uninspected host argument;
\item transport and replay stability, requiring $H$ and $C$ to preserve the same tested claim, source, windows, readback, boundary, and refusal rows;
\item nonescape for omniscience, trichotomy, quotient real equality, selected limits, countable choice, and ambient Real completeness.
\end{enumerate}
No NameCert obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:brouwerian-counterexample-carrier}. The only analytic coordinates are the tested claim $Q$, finite counterexample source $A$, window row $S$, readback row $R$, Real boundary $E$, and refusal ledger $L$.

Source exactness and windowed readback follow from the order of the displayed route. The source row $A$ is the only row that may test $Q$, while any Real or Completion-facing consumer must first read $S$ and $R$ before reaching $E$.

The refusal ledger then records a finite negative boundary. It binds each refused off-table reading to the inspected source and readback rows; it does not certify a detached host counterexample or a completed real object.

The structural rows $H,C,P,N$ only transport, replay, source, and name the same packet. Since the carrier has no coordinate for omniscience, trichotomy, quotient real equality, selected limits, countable choice, or ambient Real completeness, none of those readings can be exported as local NameCert data.
\end{proof}

\begin{theorem}[Brouwerian counterexample Real boundary]\label{thm:brouwerian-counterexample-real-boundary}
Every Real or Completion consumer of an accepted $\BrouwerianCounterexampleUp$ carrier must read the tested claim row, the finite counterexample source, the $\StreamNameUp$ windows, the $\RegSeqRatUp$ readback, and the refusal ledger before the $\RealUp$ boundary is exposed. The boundary therefore supplies finite counterexample readback only; it supplies no real trichotomy, quotient real equality, selected limit, countable-choice selector, omniscience principle, or ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with a Real or Completion-facing read of $B=(Q,A,S,R,E,L,H,C,P,N)$. The only Real-facing coordinate is $E$, and carrier admission places it after the tested claim, source, window, readback, and ledger rows.

Open the readback route. The consumer first inspects $Q$ and $A$, then obtains the finite windows through $S$ and the regular rational data through $R$. Only then can the refusal ledger $L$ say which off-table reading is not exported by the displayed source.

The endpoint row $E$ is therefore a boundary, not a completeness theorem. It records the finite Real readback surface shared with \autoref{ch:concrete-instances-real-namecert}, while the source and window discipline remain those of \autoref{ch:concrete-instances-streamname-namecert} and \autoref{ch:concrete-instances-regseqrat-namecert}.

The structural rows preserve the same route. Since the neighbouring Specker boundary of \autoref{ch:concrete-instances-specker-sequence-boundary-namecert} also refuses located-supremum escape through finite rows, the present packet can cite that style of obstruction without exporting trichotomy, quotient real equality, selected limits, countable choice, omniscience, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every $\BrouwerianCounterexampleUp$ Real or Completion read factors through a tested L10 claim row, a finite counterexample source, a StreamName window, a RegSeqRat readback, a Real boundary, a refusal ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming.}

\closureat{BrouwerianCounterexampleUp}{seedStr}

\begin{closurestatus}{\BrouwerianCounterexampleUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:brouwerian-counterexample-carrier}, \autoref{thm:brouwerian-counterexample-namecert-obligations}, and \autoref{thm:brouwerian-counterexample-real-boundary} seed the finite Brouwerian counterexample packet over tested L10 claims, finite source rows, StreamName windows, RegSeqRat readback, Real boundary, and refusal ledger data.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, real trichotomy, quotient real equality, selected limits, countable choice, omniscience principles, or ambient $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, source exactness, windowed readback, refusal-ledger exactness, transport and replay stability, Real boundary, and nonescape for BEDC.Derived.BrouwerianCounterexampleUp.}
  \constructivestory{A $\BrouwerianCounterexampleUp$ packet is generated from a tested L10 claim row, a finite counterexample source, StreamName windows, RegSeqRat readback, a Real boundary row, a refusal ledger, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert naming.}
\end{closurestatus}
