\chapter{A Concrete Naming Certificate for $\TaylorRemainderUp$}
\label{ch:concrete-instances-taylor-remainder-namecert}
\origin{human}

Following Taylor's theorem and Bishop--Bridges constructive analysis, the $\TaylorRemainderUp$ packet isolates the finite remainder-envelope data used by \autoref{ch:concrete-instances-taylor-theorem-namecert} and \autoref{ch:concrete-instances-taylormodel-namecert}. It sits after the derivative observation row of \autoref{ch:concrete-instances-derivative-namecert}, the polynomial carrier of \autoref{ch:concrete-instances-polynomial-namecert}, the regular-rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only displayed finite derivative windows, polynomial residual rows, dyadic or regular-rational error budgets, readback, transport, replay, provenance, and local naming; it does not import analytic convergence, quotient equality of functions, selected limits, or a host smooth-function theorem.

\begin{definition}[Taylor remainder carrier]
\label{def:taylor-remainder-carrier}
A $\TaylorRemainderUp$ carrier is a finite $\BHist$ packet
$$
R=(D,P,W,E,Q,S,H,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DerivativeUp$ observation row naming the center, order, domain window, and derivative budget inspected by the remainder read.
\item $P$ is the $\PolynomialUp$ row for the finite Taylor polynomial whose residual is being bounded.
\item $W$ is the finite remainder-window row. It records the endpoint or interval window, the next derivative-order budget, and the comparison side on which the residual is read.
\item $E$ is the error-envelope row, storing the displayed dyadic or regular-rational bound for the residual after $P$ has been fixed.
\item $Q$ is the $\RegSeqRatUp$ readback row through which the bound and polynomial value are exposed as regular rational names.
\item $S$ is the terminal $\RealUp$ seal reached after the derivative, polynomial, window, envelope, and regular-rational rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for derivative, polynomial, window, envelope, readback, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from every remainder-envelope request through $D,P,W,E,Q,S,H,G,N$.
\item $G$ is the $\Pkg$ provenance over $\TaylorRemainderUp$, $\DerivativeUp$, $\PolynomialUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\TaylorRemainderUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $D,P,W,E,Q,S,H,C,G,N$. It has no coordinate for an infinite Taylor series, analytic convergence, quotient equality of real functions, selected limiting values, or an ambient differentiability theorem.
\end{definition}

\begin{theorem}[Taylor remainder NameCert obligations]
\label{thm:taylor-remainder-namecert-obligations}
For every accepted $\TaylorRemainderUp$ carrier
$$
R=(D,P,W,E,Q,S,H,C,G,N),
$$
the local $\NameCert_{\TaylorRemainderUp}$ surface consists exactly of carrier admission for $R$, derivative-window exposure through $D$, polynomial-source exposure through $P$, finite remainder-window visibility through $W$, error-envelope accountability through $E$, regular-rational readback through $Q$, terminal real sealing through $S$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $G$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:taylor-remainder-carrier}. The analytic-facing rows are $D,P,W,E$: a derivative observation, a finite polynomial source, a displayed remainder window, and a residual envelope.

The readback rows are ordered. The envelope row $E$ is read only after the derivative and polynomial rows have fixed the residual being bounded, then $Q$ exposes the regular-rational readback and $S$ supplies the terminal $\RealUp$ seal.

The structural rows $H,C,G,N$ transport, replay, source, and name exactly those displayed coordinates. Since no carrier coordinate stores an infinite Taylor series, analytic convergence theorem, quotient function equality, selected limit, or host differentiability principle, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Taylor remainder Real seal handoff]
\label{thm:taylor-remainder-real-seal-handoff}
Every accepted $\TaylorRemainderUp$ remainder-envelope read factors through the finite route
$$
\DerivativeUp \longmapsto \PolynomialUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
as instantiated by $D,P,W,E,Q,S$. A $\TaylorTheoremUp$ or $\TaylorModelUp$ consumer may read the displayed residual bound only after the derivative observation, polynomial source, finite remainder window, error envelope, regular-rational readback, terminal real seal, componentwise transport, continuation replay, provenance, and local certificate rows are present.
\end{theorem}
\begin{proof}
Start with an accepted carrier $R=(D,P,W,E,Q,S,H,C,G,N)$. The derivative row $D$ fixes the observed order and domain window, while $P$ fixes the polynomial whose residual is being bounded.

The finite remainder window $W$ and envelope $E$ then bind the residual read. They record the endpoint or interval window, the derivative-order budget, and the displayed dyadic or regular-rational error bound before any consumer can cite a theorem-facing error estimate.

Finally $Q$ and $S$ route the same displayed data through regular-rational readback and the terminal Real seal. The transport, replay, provenance, and local naming rows preserve this order, so Taylor-theorem and Taylor-model consumers receive a finite remainder packet rather than analytic convergence, quotient equality, a selected limit, or an ambient smooth-function theorem.
\end{proof}
\leanstmt{BEDC.Derived.TaylorRemainderUp}

\falsifiablePrediction{Every accepted $\TaylorRemainderUp$ remainder-envelope read factors through one DerivativeUp row, one PolynomialUp row, one finite remainder-window row, one error-envelope row, one RegSeqRatUp readback row, one RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{taylor-theorem, taylormodel, derivative, polynomial, regseqrat, real: $\TaylorRemainderUp$ is not bijective to any listed sibling because it isolates the theorem-facing residual window, error-envelope row, regular-rational readback, Real seal, transport, replay, provenance, and local naming as one finite certificate.}

\closureat{TaylorRemainderUp}{seedStr}

\begin{closurestatus}{\TaylorRemainderUp}
  \constructivestory{A $\TaylorRemainderUp$ packet is generated from a DerivativeUp observation row, a PolynomialUp source row, a finite remainder window, a displayed error envelope, RegSeqRatUp readback, a RealUp seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:taylor-remainder-carrier}, \autoref{thm:taylor-remainder-namecert-obligations}, and \autoref{thm:taylor-remainder-real-seal-handoff} seed the finite Taylor residual route from derivative observations and polynomial sources to regular-rational readback and the Real seal.}
  \formalstatus{\formalTargetV}
  \leantarget{BEDC.Derived.TaylorRemainderUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not close analytic convergence, quotient equality of real functions, selected limits, ambient differentiability, Lean theorem verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, derivative-window exposure, polynomial-source exposure, finite remainder-window visibility, error-envelope accountability, regular and real readback, transport, replay, provenance, and local naming for BEDC.Derived.TaylorRemainderUp.}
\end{closurestatus}
