\chapter{A Concrete Naming Certificate for $\MengerCoverCompactnessUp$}
\label{ch:concrete-instances-menger-cover-compactness-namecert}
\origin{human}

Following Menger and Bishop--Bridges constructive compactness, the $\MengerCoverCompactnessUp$ packet records finite cover-selection compactness as displayed NameCert data. It sits after the compact metric source of \autoref{ch:concrete-instances-compactmetric-namecert}, the finite-subcover criterion of $\FiniteSubcoverCriterionUp$, the effective cover compactness surface of $\EffectiveCoverCompactnessUp$, the finite stream-window route of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names finite cover requests and finite subcover witnesses; it does not choose an open-cover subfamily from a host theorem.

\begin{definition}[Menger cover compactness carrier]
\label{def:menger-cover-compactness-carrier}
A $\MengerCoverCompactnessUp$ carrier is a finite $\BHist$ packet
$$
M=(K,R,B,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact metric source row read through $\CompactMetricUp$.
\item $R$ is a finite sequence of cover requests, each naming one inspected finite open-cover window and its tolerance budget.
\item $B$ is the $\ProbeBundle$ finite-subcover ledger, recording for every request in $R$ the selected finite probe rows, membership witnesses, and cover verification.
\item $W$ is the $\StreamNameUp$ finite-window readback row used to inspect the cover requests and probe names.
\item $Q$ is the $\RegSeqRatUp$ readback row for the rational radii and comparison margins attached to the selected probes.
\item $E$ is the terminal $\RealUp$ seal row reached only after $K,R,B,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the compact metric source, cover requests, finite-subcover ledger, stream windows, regular-rational readback, Real seal, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from each cover request through $K,R,B,W,Q,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\MengerCoverCompactnessUp$, $\CompactMetricUp$, $\FiniteSubcoverCriterionUp$, $\EffectiveCoverCompactnessUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\ProbeBundle$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MengerCoverCompactnessUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $K,R,B,W,Q,E,H,C,P,N$. It contains no coordinate for countable choice, an arbitrary open-cover selector, quotient real equality, a host compactness theorem, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Menger cover compactness NameCert obligations]
\label{thm:menger-cover-compactness-namecert-obligations}
For every accepted $\MengerCoverCompactnessUp$ carrier $M=(K,R,B,W,Q,E,H,C,P,N)$, the local $\NameCert_{\MengerCoverCompactnessUp}$ surface consists exactly of compact metric source exposure through $K$; finite cover-request exposure through $R$; $\ProbeBundle$ finite-subcover verification through $B$; stream-window readback through $W$; regular-rational readback through $Q$; terminal Real sealing through $E$; componentwise $\hsame$ transport through $H$; displayed $\Cont$ replay through $C$; $\Pkg$ provenance through $P$; and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:menger-cover-compactness-carrier}. The compact metric source, request list, and finite-subcover ledger are exactly $K,R,B$.

The readback rows $W,Q,E$ are downstream of those finite cover rows. They expose the finite stream windows, rational radius data, and terminal real-name seal only after each selected subcover witness has been displayed.

Transport, replay, provenance, and local naming through $H,C,P,N$ preserve the same finite route. Since the carrier has no row for countable choice, host open-cover selection, quotient real equality, or ambient completeness, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Menger cover compactness finite cover selection]
\label{thm:menger-cover-compactness-finite-cover-selection}
Every finite cover-selection consumer of an accepted $\MengerCoverCompactnessUp$ carrier must read the compact metric source $K$, then the finite request sequence $R$, then the $\ProbeBundle$ finite-subcover row $B$, before it can inspect the $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ readback rows. The route factors through $\FiniteSubcoverCriterionUp$ and $\EffectiveCoverCompactnessUp$ as finite certificate surfaces, not as a choice-selected open-cover theorem.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $M=(K,R,B,W,Q,E,H,C,P,N)$. The row $K$ supplies the compact metric source, while $R$ lists the only cover requests visible to the consumer.

For each request, $B$ stores the finite probe rows and verification that they cover the inspected window. Thus the consumer receives finite subcover evidence before any stream, rational, or real readback row is exposed.

Finally $W,Q,E,H,C,P,N$ read, transport, replay, source, and name that finite evidence. The route cannot introduce an arbitrary open-cover selector or countable-choice schedule, because no such coordinate occurs in the carrier.
\end{proof}

\begin{theorem}[Menger cover compactness Real-seal nonescape]
\label{thm:menger-cover-compactness-real-seal-nonescape}
No $\RealUp$ consumer of an accepted $\MengerCoverCompactnessUp$ packet can bypass the displayed route
$$
\CompactMetricUp,\ R,\ \ProbeBundle,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp .
$$
The terminal Real seal $E$ is public only after the compact metric source, finite cover requests, finite-subcover ledger, stream windows, and rational radius readback have all been displayed.
\end{theorem}
\begin{proof}
Read the finite cover-selection theorem \autoref{thm:menger-cover-compactness-finite-cover-selection}. It places $K,R,B$ before the stream, rational, and Real rows.

The terminal seal $E$ is not an independent Real object. It is reached only through $W$ and $Q$, which are themselves attached to the finite request and finite-subcover rows.

Consequently every accepted Real-facing read must pass through the displayed compactness packet and its structural rows $H,C,P,N$. The excluded host compactness, selected subcover, countable-choice, quotient-equality, and ambient-completeness claims are not exported.
\end{proof}

\falsifiablePrediction{Every accepted $\MengerCoverCompactnessUp$ Real or Completion consumer exposes the compact metric source, finite cover-request sequence, $\ProbeBundle$ finite-subcover row, stream windows, regular-rational readback, Real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ before using finite cover-selection compactness.}

\independenceWitness{compactmetric, finite-subcover-criterion, effective-cover-compactness, streamname, regseqrat, real: $\MengerCoverCompactnessUp$ is not bijective to any listed sibling because this packet binds compact metric source rows, finite cover requests, finite ProbeBundle subcover witnesses, stream windows, rational readback, Real sealing, transport, replay, provenance, and local naming into one cover-selection certificate.}

\closureat{MengerCoverCompactnessUp}{seedStr}

\begin{closurestatus}{\MengerCoverCompactnessUp}
  \constructivestory{A $\MengerCoverCompactnessUp$ packet is generated from a CompactMetricUp source row, finite cover requests, ProbeBundle finite-subcover rows, StreamNameUp windows, RegSeqRatUp radius readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:menger-cover-compactness-carrier}, \autoref{thm:menger-cover-compactness-namecert-obligations}, \autoref{thm:menger-cover-compactness-finite-cover-selection}, and \autoref{thm:menger-cover-compactness-real-seal-nonescape} seed the finite cover-selection NameCert route for compact metric Real and Completion consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim arbitrary open-cover compactness, countable-choice subcover selection, quotient real equality, ambient $\RealUp$ completeness, Lean theorem checking, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact metric source exposure, finite cover-request exposure, ProbeBundle finite-subcover verification, StreamName readback, RegSeqRat radius readback, Real sealing, transport, replay, provenance, and local naming for BEDC.Derived.MengerCoverCompactnessUp.}
\end{closurestatus}
