\chapter{A Concrete Naming Certificate for $\CompactUniformOscillationWindowUp$}
\label{ch:concrete-instances-compact-uniform-oscillation-window-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\CompactUniformOscillationWindowUp$ packet records the finite-net and finite oscillation-window route used by compact uniform continuity. It is the concrete landing for the vision of \autoref{ch:visions-compact-uniform-continuity}, sitting between the compact oscillation packet of \autoref{ch:concrete-instances-compact-uniform-oscillation-namecert} and the finite oscillation partition packet of \autoref{ch:concrete-instances-finite-oscillation-partition-namecert}. It also reads compact metric source data from \autoref{ch:concrete-instances-compactmetric-namecert}, continuous graph data from \autoref{ch:concrete-instances-continuousmap-namecert}, uniform-modulus data from \autoref{ch:concrete-instances-uniformmodulus-namecert}, finite windows from \autoref{ch:concrete-instances-streamname-namecert}, regular rational readback from \autoref{ch:concrete-instances-regseqrat-namecert}, dyadic tolerance from \autoref{ch:concrete-instances-dyadicratcore-namecert}, and terminal real-name sealing from \autoref{ch:concrete-instances-real-namecert}. The packet does not claim open-cover compactness, selected extrema, quotient function equality, unbounded partition search, or ambient completeness.

\begin{definition}[Compact uniform oscillation window carrier]
\label{def:compact-uniform-oscillation-window-carrier}
A $\CompactUniformOscillationWindowUp$ carrier is a finite $\BHist$ packet
$$
Q=(K,F,U,O,M,B,W,R,D,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact finite-net source row, read through the accepted $\CompactMetricUp$ finite-net surface.
\item $F$ is the continuous graph row, exposing the displayed $\ContinuousMapUp$ observations consumed by the compact-uniform route.
\item $U$ is the $\UniformModulusUp$ ledger, recording tolerance requests and source-radius responses.
\item $O$ is the $\CompactUniformOscillationUp$ oscillation-bound row over the same compact source and graph rows.
\item $M$ is the finite mesh row, listing the compact finite-net cells or interval cells used by the oscillation window.
\item $B$ is the finite oscillation-window row supplied by $\FiniteOscillationPartitionUp$, recording the cellwise bound and refinement readback.
\item $W$ is the $\StreamNameUp$ finite-window row for source and target observations.
\item $R$ is the $\RegSeqRatUp$ readback row attached to those windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row shared by $U,O,M,B,W,R$.
\item $S$ is the terminal $\RealUp$ seal row reached only after the compact finite-net, graph, modulus, oscillation, mesh, window, readback, and tolerance rows have been displayed.
\item $H$ records componentwise $\hsame$ transport for all analytic and structural rows.
\item $C$ records displayed $\Cont$ replay through
$$
K,F,U,O,M,B,W,R,D,S \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CompactUniformOscillationWindowUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\UniformModulusUp$, $\CompactUniformOscillationUp$, $\FiniteOscillationPartitionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CompactUniformOscillationWindowUp}$ row.
\end{enumerate}
The carrier compares accepted packets only through these rows. It has no coordinate for open-cover compactness, selected extrema, quotient equality of maps, unbounded partition search, choice-selected refinements, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Compact uniform oscillation window NameCert obligations]
\label{thm:compact-uniform-oscillation-window-namecert-obligations}
For every accepted $\CompactUniformOscillationWindowUp$ carrier
$$
Q=(K,F,U,O,M,B,W,R,D,S,H,C,P,N),
$$
the local $\NameCert_{\CompactUniformOscillationWindowUp}$ surface consists exactly of compact finite-net exposure through $K$, continuous graph exposure through $F$, uniform-modulus accounting through $U$, compact oscillation-bound exposure through $O$, finite mesh exposure through $M$, finite oscillation-window exposure through $B$, StreamName window exposure through $W$, RegSeqRat readback through $R$, DyadicRatCore tolerance accounting through $D$, Real sealing through $S$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:compact-uniform-oscillation-window-carrier}. The compact-uniform rows are $K,F,U,O$, and the finite oscillation-window rows are $M,B,W,R,D,S$.

The compact source is finite at the point of consumption. The row $K$ supplies finite-net data, $F$ supplies the displayed continuous graph, and $U$ records the tolerance-only modulus ledger used by the compact-uniform read.

The oscillation window is then read through $O,M,B,W,R,D,S$. The compact oscillation-bound row and finite mesh row determine which cellwise windows are visible, while the stream, rational, dyadic, and real rows provide the finite readback and terminal seal.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since none of the excluded compactness, selection, quotient, unbounded-search, or completeness principles is a carrier coordinate, no NameCert obligation can project one.
\end{proof}

\begin{theorem}[Compact uniform oscillation window modulus handoff]
\label{thm:compact-uniform-oscillation-window-modulus-handoff}
Every compact-uniform-continuity or integration-facing consumer of an accepted $\CompactUniformOscillationWindowUp$ packet receives a finite oscillation modulus through
$$
\CompactMetricUp,\ \ContinuousMapUp,\ \UniformModulusUp,\ \CompactUniformOscillationUp,\ \FiniteOscillationPartitionUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp \longmapsto H,C,P,N .
$$
The handoff reads compact finite nets, continuous graph observations, the tolerance-only modulus ledger, compact oscillation bounds, finite mesh cells, cellwise oscillation windows, finite stream windows, regular rational readback, dyadic tolerance, and terminal Real sealing before any structural replay is available.
\end{theorem}
\begin{proof}
Apply \autoref{thm:compact-uniform-oscillation-window-namecert-obligations}. A consumer must expose $K,F,U,O,M,B,W,R,D,S$ before it can use the transport, replay, provenance, or local naming rows.

The modulus handoff is finite because $K$ and $M$ fix the finite source and cell rows. The tolerance request is answered through $U$ and $D$, while $O$ and $B$ record the compact oscillation and cellwise window bounds.

The readback remains certificate-local. The rows $W,R,S$ expose finite observations, regular rational readback, and the terminal real-name seal, and $H,C,P,N$ preserve that same route.

Thus the packet exports a finite oscillation modulus for compact-uniform readers. It does not export open-cover compactness, selected extrema, quotient function equality, unbounded partition search, choice-selected refinements, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every accepted $\CompactUniformOscillationWindowUp$ reader that claims a compact finite oscillation modulus while omitting one of the compact finite-net, continuous graph, uniform-modulus, compact oscillation-bound, finite mesh, cellwise window, StreamName, RegSeqRat, DyadicRatCore, Real seal, hsame transport, Cont replay, Pkg provenance, or local naming rows refutes the packet.}

\independenceWitness{compact-uniform-oscillation, finite-oscillation-partition, compactmetric, continuousmap, uniformmodulus, streamname, regseqrat, dyadicratcore, real: $\CompactUniformOscillationWindowUp$ is not bijective with any listed sibling because it joins compact finite-net source data, continuous graph rows, uniform-modulus accounting, compact oscillation bounds, finite oscillation partitions, finite readback, Real sealing, transport, replay, provenance, and local naming as one packet.}

\closureat{CompactUniformOscillationWindowUp}{seedStr}

\begin{closurestatus}{\CompactUniformOscillationWindowUp}
  \constructivestory{A $\CompactUniformOscillationWindowUp$ packet is generated from compact finite-net source data, ContinuousMap graph rows, a UniformModulus ledger, a CompactUniformOscillation bound row, a finite mesh row, a FiniteOscillationPartition window row, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:compact-uniform-oscillation-window-carrier}, \autoref{thm:compact-uniform-oscillation-window-namecert-obligations}, and \autoref{thm:compact-uniform-oscillation-window-modulus-handoff} seed the compact finite-net and finite oscillation-window route for compact-uniform-continuity and integration-facing consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, selected extrema, quotient function equality, unbounded partition search, choice-selected refinements, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-net exposure, continuous graph exposure, uniform-modulus accounting, compact oscillation-bound exposure, finite mesh exactness, finite oscillation-window accounting, finite readback, tolerance accounting, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.CompactUniformOscillationWindowUp.}
\end{closurestatus}
