\chapter{A Concrete Naming Certificate for $\BishopEquicontinuityPrincipleUp$}
\label{ch:concrete-instances-bishop-equicontinuity-principle-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\BishopEquicontinuityPrincipleUp$ packet records the finite-family form of equicontinuity used for located real intervals and regular Cauchy real-name maps. It sits after the Cauchy-continuous map object of \autoref{ch:concrete-instances-cauchy-continuous-function-namecert}, the located interval uniform-Cauchy route of \autoref{ch:concrete-instances-located-interval-uniform-cauchy-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names the textbook finite-means equicontinuity handoff without importing host function equality, open-cover compactness, selected limits, quotient real equality, or ambient $\RealUp$ completeness.

\begin{definition}[Bishop equicontinuity principle carrier]
\label{def:bishop-equicontinuity-principle-carrier}
A $\BishopEquicontinuityPrincipleUp$ carrier is a finite $\BHist$ packet
$$
E=(F,I,M,U,W,R,D,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the finite family row, listing the accepted family indices and the familywise consumer route without exposing a host function space.
\item $I$ is the located interval source row, read through the displayed interval and located endpoint data used by the family.
\item $M$ is the $\CauchyContinuousFunctionUp$ row for each family member, recording the source-window, tolerance, graph, image-name, and real-seal route of the member.
\item $U$ is the uniform-Cauchy handoff row supplied over the same located interval source; it records the common finite tolerance route consumed by the family.
\item $W$ is the $\StreamNameUp$ finite-window row for source and image observations.
\item $R$ is the $\RegSeqRatUp$ readback row attached to the same finite windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row, recording the dyadic comparison budget used by the family and the common handoff.
\item $S$ is the terminal $\RealUp$ seal row reached only after $F,I,M,U,W,R,D$ have fixed the finite family route.
\item $H$ records componentwise $\hsame$ transport for the family, interval, map, uniform-Cauchy, window, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through the finite route
$$
F,I,M,U \longmapsto W,R,D,S,H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\BishopEquicontinuityPrincipleUp$, $\CauchyContinuousFunctionUp$, $\LocatedIntervalUniformCauchyUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopEquicontinuityPrincipleUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for host equality of functions, open-cover compactness, selected pointwise limits, quotient equality of real names, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bishop equicontinuity principle NameCert obligations]
\label{thm:bishop-equicontinuity-principle-namecert-obligations}
For every accepted $\BishopEquicontinuityPrincipleUp$ carrier
$$
E=(F,I,M,U,W,R,D,S,H,C,P,N),
$$
the local $\NameCert_{\BishopEquicontinuityPrincipleUp}$ surface consists exactly of carrier admission for the displayed rows, finite family exposure through $F$, located interval exposure through $I$, CauchyContinuousFunction exposure through $M$, uniform-Cauchy handoff exposure through $U$, StreamName window exposure through $W$, RegSeqRat readback through $R$, DyadicRatCore tolerance accounting through $D$, Real sealing through $S$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-equicontinuity-principle-carrier}. The analytic rows are the finite family $F$, the located interval source $I$, the Cauchy-continuous member rows $M$, the uniform-Cauchy handoff $U$, and the window, readback, tolerance, and seal rows $W,R,D,S$.

The family and interval obligations are finite. The row $F$ fixes the accepted family indices, while $I$ fixes the located interval source on which every member row is read.

The map and handoff obligations are then read from $M$ and $U$. Each member exposes only the CauchyContinuousFunction route, and the common handoff supplies the tolerance route that a downstream equicontinuity consumer may share.

Finally $H,C,P,N$ transport, replay, source, and name exactly the displayed rows. Since the carrier has no coordinate for host function equality, open-cover compactness, selected limits, quotient real-name equality, choice, or ambient completeness, those objects cannot appear as local obligations.
\end{proof}

\begin{theorem}[Bishop equicontinuity principle uniform-Cauchy handoff]
\label{thm:bishop-equicontinuity-principle-uniform-cauchy-handoff}
Every equicontinuity-facing consumer of an accepted $\BishopEquicontinuityPrincipleUp$ carrier receives the finite handoff
$$
\CauchyContinuousFunctionUp,\ \LocatedIntervalUniformCauchyUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp \longmapsto H,C,P,N .
$$
The consumer may read the finite family row, located interval source, CauchyContinuousFunction rows, common uniform-Cauchy handoff, finite windows, regular rational readback, dyadic tolerance budget, terminal Real seal, transport, replay, provenance, and local NameCert. It cannot bypass those rows by comparing host functions, selecting pointwise limits, importing open-cover compactness, or appealing to ambient completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bishop-equicontinuity-principle-namecert-obligations}. Any accepted consumer must open $F,I,M,U,W,R,D,S$ before the structural rows $H,C,P,N$ are available.

The common equicontinuity route is controlled by $U$ over the same located interval row $I$. The finite family row $F$ determines which member rows in $M$ are being read, while $W,R,D,S$ expose only finite windows, rational readback, dyadic tolerance, and the terminal real-name seal.

The displayed $\Cont$ replay preserves that order. Hence a downstream uniform-Cauchy or compact-interval consumer receives a finite BEDC handoff rather than an external function-space principle, selected limit argument, open-cover compactness theorem, quotient comparison, or Real completeness claim.
\end{proof}

\falsifiablePrediction{Every accepted $\BishopEquicontinuityPrincipleUp$ equicontinuity read factors through one finite family row, one located interval source row, CauchyContinuousFunction member rows, one uniform-Cauchy handoff row, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a terminal RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchy-continuous-function, located-interval-uniform-cauchy, streamname, regseqrat, dyadicratcore, real: $\BishopEquicontinuityPrincipleUp$ is not bijective with any listed sibling because it jointly carries a finite family route, located interval source, Cauchy-continuous member rows, a common uniform-Cauchy handoff, finite windows, rational readback, dyadic tolerance, Real sealing, transport, replay, provenance, and local naming.}

\closureat{BishopEquicontinuityPrincipleUp}{seedStr}

\begin{closurestatus}{\BishopEquicontinuityPrincipleUp}
  \constructivestory{A $\BishopEquicontinuityPrincipleUp$ packet is generated from a finite family row, located interval source, CauchyContinuousFunction member rows, a uniform-Cauchy handoff, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-equicontinuity-principle-carrier}, \autoref{thm:bishop-equicontinuity-principle-namecert-obligations}, and \autoref{thm:bishop-equicontinuity-principle-uniform-cauchy-handoff} seed the finite family equicontinuity route over located intervals, Cauchy-continuous map rows, uniform-Cauchy handoff, window readback, dyadic tolerance, Real sealing, transport, replay, provenance, and local naming.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim host function equality, open-cover compactness, selected pointwise limits, quotient equality of real names, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite family exposure, located interval exposure, CauchyContinuousFunction member exposure, uniform-Cauchy handoff exactness, finite-window replay, RegSeqRat readback, dyadic tolerance accounting, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopEquicontinuityPrincipleUp.}
\end{closurestatus}
