\chapter{A Concrete Naming Certificate for $\BishopCauchyCompletionPairUp$}
\label{ch:concrete-instances-bishop-cauchy-completion-pair-namecert}
\origin{human}

Following Bishop and Bridges, the $\BishopCauchyCompletionPairUp$ packet records the finite pair interface by which a displayed metric source and its dense Cauchy-name completion route are read before any $\RealUp$ or completion-facing consumer may inspect a seal. It sits beside the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}, and the oscillation-bound route of \autoref{ch:concrete-instances-cauchyoscillation-namecert}. The packet is a NameCert interface for the completion pair, not a quotient completion, selected representative, host limit, countable-choice schedule, or ambient completeness theorem.

\begin{definition}[Bishop Cauchy completion-pair carrier]
\label{def:bishop-cauchy-completion-pair-carrier}
A $\BishopCauchyCompletionPairUp$ carrier is a finite $\BHist$ packet
$$
K=(M,D,W,R,T,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source metric row, naming the displayed points, distance evidence, and finite request surface of the pre-completion space.
\item $D$ is the dense-embedding row, recording how source points are inserted into the completion route before any completed endpoint is inspected.
\item $W$ is the $\StreamNameUp$ finite-window row used to inspect the Cauchy names attached to the source and embedded rows.
\item $R$ is the $\RegSeqRatUp$ regular-Cauchy seal over the windows in $W$.
\item $T$ is the $\DyadicRatCoreUp$ tolerance ledger controlling the comparison precision for $W$ and $R$.
\item $E$ is the $\RealUp$ seal handoff, available only after $M,D,W,R,T$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the metric source, dense embedding, finite windows, regular-Cauchy seal, dyadic ledger, Real seal, replay, provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay of the route from $M$ and $D$ through $W,R,T,E,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\BishopCauchyCompletionPairUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\CauchyOscillationUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BishopCauchyCompletionPairUp}$ row.
\end{enumerate}
The carrier stores no quotient class, selected limit, host equality proof, countable-choice schedule, hidden completion point, or ambient completeness witness.
\end{definition}

\begin{theorem}[Bishop Cauchy completion-pair NameCert obligations]
\label{thm:bishop-cauchy-completion-pair-namecert-obligations}
For every accepted $\BishopCauchyCompletionPairUp$ carrier $K=(M,D,W,R,T,E,H,C,P,N)$, the local $\NameCert_{\BishopCauchyCompletionPairUp}$ surface consists exactly of the following five obligation families:
\begin{enumerate}
\item carrier admission for the displayed metric source row $M$, dense-embedding row $D$, $\StreamNameUp$ finite windows $W$, $\RegSeqRatUp$ regular-Cauchy seal $R$, $\DyadicRatCoreUp$ tolerance ledger $T$, and $\RealUp$ seal handoff $E$;
\item dense-source routing, requiring every completion-facing read to pass from $M$ through $D$ before any window, readback, tolerance, or seal row is consumed;
\item regular-Cauchy exactness, requiring $W,R,T$ to be read as one finite window-and-tolerance packet before $E$ is public;
\item transport and replay stability for the same rows under componentwise $\hsame$ and displayed $\Cont$;
\item provenance and local naming exhaustion through $P$ and $N$, with no quotient completion, selected representative, host limit, countable choice, or ambient completeness row exported by the packet.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bishop-cauchy-completion-pair-carrier}. Its analytic rows are exactly $M,D,W,R,T,E$, and its structural rows are exactly $H,C,P,N$.

The source route begins at $M$ and $D$. A completion-facing consumer may inspect the metric source and its dense embedding, but neither row contains a completed endpoint or quotient representative.

The Cauchy-name route then opens the finite window $W$, regular readback $R$, and dyadic tolerance ledger $T$. These rows are the only data from which the Real seal handoff $E$ can be reached.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route. Since the carrier has no coordinate for the refused host objects, the five listed obligation families exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bishop Cauchy completion-pair routed seal]
\label{thm:bishop-cauchy-completion-pair-routed-seal}
Every $\RealUp$ or completion-facing consumer of an accepted $\BishopCauchyCompletionPairUp$ packet reads the terminal seal only through the finite route
$$
M \longmapsto D \longmapsto W \longmapsto R \longmapsto T \longmapsto E.
$$
Equivalently, the source metric data, dense embedding, $\StreamNameUp$ windows, $\RegSeqRatUp$ regular-Cauchy seal, and $\DyadicRatCoreUp$ tolerance ledger must all be displayed before the $\RealUp$ seal handoff is public.
\end{theorem}
\begin{proof}
The NameCert obligations of \autoref{thm:bishop-cauchy-completion-pair-namecert-obligations} order the carrier rows. Source admission exposes $M$, and dense-source routing forces the embedding row $D$ to be read before the Cauchy-name rows are interpreted.

Regular-Cauchy exactness then ties $W,R,T$ into one finite packet. The seal row $E$ is downstream of that packet, so a consumer has no route to $E$ that bypasses the displayed windows, readback, or tolerance ledger.

Transport, replay, provenance, and naming preserve the same route componentwise. Thus the exported seal is a finite completion-pair handoff rather than a quotient completion, selected representative, host limit, choice principle, or ambient completeness witness.
\end{proof}

\falsifiablePrediction{A claimed $\BishopCauchyCompletionPairUp$ consumer that reaches $\RealUp$ or a completion-facing seal without displaying $M,D,W,R,T$ refutes the carrier.}

\independenceWitness{dyadicratcore, streamname, regseqrat, real, cauchyoscillation: no listed sibling is bijective to $\BishopCauchyCompletionPairUp$ because the packet jointly carries a source metric row, dense embedding, finite windows, regular-Cauchy seal, dyadic tolerance ledger, Real seal handoff, transport, replay, provenance, and local NameCert row.}

\closureat{BishopCauchyCompletionPairUp}{seedStr}

\begin{closurestatus}{\BishopCauchyCompletionPairUp}
  \constructivestory{A $\BishopCauchyCompletionPairUp$ packet is generated from source metric data, a dense embedding row, StreamName finite windows, RegSeqRat regular-Cauchy seal, DyadicRatCore tolerance ledger, Real seal handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-cauchy-completion-pair-carrier}, \autoref{thm:bishop-cauchy-completion-pair-namecert-obligations}, and \autoref{thm:bishop-cauchy-completion-pair-routed-seal} seed the finite Bishop completion-pair route from metric source and dense embedding through windows, readback, tolerances, and Real seal handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient completions, selected representatives, countable choice, host real equality, ambient Real completeness, Lean verification, or bridge checking for $\BishopCauchyCompletionPairUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, dense-source routing, regular-Cauchy exactness, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.BishopCauchyCompletionPairUp.}
\end{closurestatus}
