\chapter{A Concrete Naming Certificate for $\RealCauchyFilterBasisUp$}
\label{ch:concrete-instances-real-cauchy-filter-basis-namecert}
\origin{human}

Following Bishop and Bridges on constructive real completion, the $\RealCauchyFilterBasisUp$ packet records the finite filter-basis route by which regular rational sequence data, finite stream windows, and dyadic tolerance rows are read before a terminal $\RealUp$ seal is exposed. It sits between the Cauchy-filter surface of \autoref{ch:concrete-instances-cauchyfilter-namecert}, the finite window naming of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the real-name boundary of \autoref{ch:concrete-instances-real-namecert}. The packet names a finite basis for Real-facing completion reads; it is not a quotient-stream construction, a selected limit, a countable-choice principle, or an ambient completeness theorem.

\begin{definition}[Real Cauchy filter-basis carrier]
\label{def:real-cauchy-filter-basis-carrier}
A $\RealCauchyFilterBasisUp$ carrier is a finite $\BHist$ packet
$$
B=(F,W,D,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the basis row, recording the finite Cauchy-filter basic neighborhoods and their inclusion reads.
\item $W$ is the finite tail-window row, recording the $\StreamNameUp$ windows and requested indices used to inspect each basis neighborhood.
\item $D$ is the dyadic tolerance row, recording the $\DyadicRatCoreUp$ radius, denominator budget, and slack comparison attached to each window.
\item $R$ is the $\RegSeqRatUp$ readback row, repacking the accepted tail-window observations as regular rational sequence data.
\item $Q$ is the terminal $\RealUp$ seal row, visible only after $F,W,D,R$ have displayed the basis, windows, tolerances, and regular-sequence readback.
\item $H$ stores componentwise $\hsame$ transport for the basis, tail-window, dyadic tolerance, readback, Real seal, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a Real-facing precision request through the basis row, finite windows, dyadic tolerance ledger, regular-sequence readback, and terminal seal.
\item $P$ records $\Pkg$ provenance over $\RealCauchyFilterBasisUp$, $\CauchyFilterUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ data.
\item $N$ is the local $\NameCert_{\RealCauchyFilterBasisUp}$ row.
\end{enumerate}
Accepted carriers are compared only through $F,W,D,R,Q,H,C,P,N$. There is no coordinate for quotient streams, selected representatives, selected limits, countable choice, host completeness, or ambient $\RealUp$ equality.
\end{definition}

\begin{theorem}[Real Cauchy filter-basis NameCert obligations]
\label{thm:real-cauchy-filter-basis-namecert-obligations}
For every accepted $\RealCauchyFilterBasisUp$ carrier $B=(F,W,D,R,Q,H,C,P,N)$, the local $\NameCert_{\RealCauchyFilterBasisUp}$ surface consists exactly of carrier admission, basis-neighborhood exposure, finite tail-window exactness, dyadic-tolerance exactness, $\RegSeqRatUp$ readback, $\RealUp$ seal descent, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local naming row for the same finite packet. No local obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $B=(F,W,D,R,Q,H,C,P,N)$. The carrier definition exposes exactly the basis, window, tolerance, readback, seal, transport, replay, provenance, and naming rows.

The basis-facing obligations are $F,W,D$. A consumer must first read the basic neighborhood, then the finite stream window that inspects it, and then the dyadic radius and slack comparison attached to that window.

The completion-facing obligations are $R,Q,H,C,P,N$. They repack the displayed data as regular rational readback, seal it as a Real-facing row, transport and replay the same route, cite its provenance, and name it locally. Since the carrier has no further coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Real Cauchy filter-basis RegSeqRat handoff]
\label{thm:real-cauchy-filter-basis-regseqrat-handoff}
Every $\RegSeqRatUp$ read exported by an accepted $\RealCauchyFilterBasisUp$ carrier factors through
$$
\CauchyFilterUp,\StreamNameUp,\DyadicRatCoreUp \longmapsto \RegSeqRatUp
$$
inside the displayed rows $F,W,D,R$. Thus the regular rational sequence readback is available only after the basis neighborhood, finite tail window, and dyadic tolerance ledger have been displayed.
\end{theorem}
\begin{proof}
Begin with a consumer asking for the regular rational readback row $R$. By the carrier definition, the only route to $R$ passes through the basis row $F$, the window row $W$, and the dyadic tolerance row $D$.

The row $F$ names the Cauchy-filter basic neighborhood. The row $W$ records the finite stream window used to inspect the tail of that neighborhood, and $D$ records the dyadic radius and comparison budget consumed by the read.

The row $R$ then repacks exactly those displayed observations as $\RegSeqRatUp$ data. The route therefore has no coordinate for quotient streams, selected representatives, selected limits, countable choice, or host completeness.
\end{proof}

\begin{theorem}[Real Cauchy filter-basis completion ledger]
\label{thm:real-cauchy-filter-basis-completion-ledger}
For every accepted carrier $B=(F,W,D,R,Q,H,C,P,N)$, a completion-facing read consumes the finite ledger
$$
F,W,D,R,Q,H,C,P,N
$$
in that order: basis neighborhood, tail window, dyadic tolerance, regular rational readback, Real seal, transport, replay, provenance, and local naming. The ledger exports no quotient-stream equality, chosen representative, selected limit, countable-choice schedule, host-completeness theorem, or ambient Real equality.
\end{theorem}
\begin{proof}
Read the displayed continuation row $C$. It routes a Real-facing precision request through $F,W,D,R,Q$ before the structural rows are consumed.

The first four rows form the finite completion ledger. They display the basis neighborhood, the inspected window, the dyadic tolerance comparison, and the regular rational readback.

The row $Q$ is downstream of that ledger, while $H,P,N$ preserve, source, and name the same data. Because the excluded objects do not occur as carrier coordinates, the completion-facing read cannot export them.
\end{proof}

\begin{theorem}[Real Cauchy filter-basis Real seal]
\label{thm:real-cauchy-filter-basis-real-seal}
The $\RealUp$ seal of an accepted $\RealCauchyFilterBasisUp$ packet is terminal for the displayed basis route: every public read of $Q$ factors through $F,W,D,R$ and then through $H,C,P,N$. Consequently the seal certifies only the finite Real-facing basis packet, not quotient completion equality, selected limits, countable choice, host completeness, or ambient equality of real names.
\end{theorem}
\begin{proof}
Let a public consumer read the terminal row $Q$. The carrier definition places $Q$ after the basis, window, dyadic, and regular readback rows, so the consumer must first expose $F,W,D,R$.

Componentwise transport $H$ and replay $C$ keep the public read on that same finite route. Provenance $P$ and local naming $N$ identify the packet without adding a completion principle.

Thus the terminal seal is a Real-facing row of the displayed carrier. It is not a quotient equality, selected limit, choice schedule, host-completeness theorem, or ambient equality proof.
\end{proof}

\falsifiablePrediction{Every $\RealCauchyFilterBasisUp$ Real-facing read factors through a CauchyFilter basis row, StreamName finite tail windows, a DyadicRatCore tolerance row, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchyfilter, streamname, dyadicratcore, regseqrat, real: $\RealCauchyFilterBasisUp$ is not bijective to any listed sibling because it jointly carries basis neighborhoods, finite tail windows, dyadic tolerance comparisons, regular rational readback, terminal Real sealing, transport, replay, provenance, and local naming.}

\closureat{RealCauchyFilterBasisUp}{seedStr}

\begin{closurestatus}{\RealCauchyFilterBasisUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:real-cauchy-filter-basis-carrier}, \autoref{thm:real-cauchy-filter-basis-namecert-obligations}, \autoref{thm:real-cauchy-filter-basis-regseqrat-handoff}, \autoref{thm:real-cauchy-filter-basis-completion-ledger}, and \autoref{thm:real-cauchy-filter-basis-real-seal} seed the finite route from Cauchy-filter basis rows to regular rational readback and the terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient streams, selected representatives, selected limits, countable choice, host completeness, ambient $\RealUp$ equality, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, tail-window exactness, dyadic-tolerance exactness, RegSeqRat readback, Real seal descent, transport, replay, provenance, and local naming for BEDC.Derived.RealCauchyFilterBasisUp.}
  \constructivestory{A $\RealCauchyFilterBasisUp$ packet is generated from a CauchyFilter basis row, finite StreamName tail windows, DyadicRatCore tolerance data, RegSeqRat readback, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
