\chapter{A Concrete Naming Certificate for $\InitialUniformityUp$}
\label{ch:concrete-instances-initial-uniformity-namecert}
\origin{human}

Following Bourbaki on uniform structures and initial uniformities, the $\InitialUniformityUp$ packet names the finite pullback-uniformity route determined by a displayed map into a target uniform space. It sits after the Real-induced uniformity of \autoref{ch:concrete-instances-real-uniform-structure-namecert}, the abstract uniform entourage basis of \autoref{ch:concrete-instances-uniform-entourage-basis-namecert}, and the completion-facing handoff of \autoref{ch:concrete-instances-uniform-space-completion-namecert}. The packet records only source rows, target entourages, displayed maps, pulled-back entourage rows, transport, replay, provenance, and local naming; it is not an ambient topology, quotient uniformity, selected representative principle, open-cover compactness theorem, or countable-choice device.

\begin{definition}[InitialUniformity carrier]
\label{def:initial-uniformity-carrier}
An $\InitialUniformityUp$ carrier is a finite $\BHist$ packet
$$
I=(S,T,F,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source carrier row. It records the points or names on which the pulled-back uniformity is being inspected.
\item $T$ is the target uniformity row. It exposes the finite target-entourage requests admitted by the target $\UniformSpaceUp$ or by a basis packet such as $\UniformEntourageBasisUp$.
\item $F$ is the displayed map row. It names the finite graph, readback, or continuation by which a source request is sent into the target carrier before an entourage is tested.
\item $E$ is the pulled-back entourage row. Each entry records a target entourage from $T$ together with the displayed source-pair request whose two $F$-images are tested against that target entourage.
\item $H$ records componentwise $\hsame$ transport for $S,T,F,E,C,P,N$.
\item $C$ records displayed $\Cont$ replay from a source-pair request through $F$ and then through the target-entourage read in $T$.
\item $P$ is the $\Pkg$ provenance over $\InitialUniformityUp$, $\UniformSpaceUp$, $\UniformEntourageBasisUp$, $\UniformSpaceCompletionUp$, $\RealUniformStructureUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\InitialUniformityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $S,T,F,E,H,C,P,N$. It has no coordinate for an ambient topology on $S$, a quotient uniformity, a selected representative family, a host continuity theorem, open-cover compactness, countable choice, or external completeness.
\end{definition}

\begin{theorem}[InitialUniformity pullback entourage stability]
\label{thm:initial-uniformity-pullback-entourage-stability}
Let $I=(S,T,F,E,H,C,P,N)$ be an accepted $\InitialUniformityUp$ carrier. If two displayed source-pair requests are componentwise $\hsame$ through $H$, and the target-entourage read is replayed through the displayed $\Cont$ route $C$, then the pulled-back entourage row $E$ returns the same accepted pullback read. Thus pullback-entourage stability is internal to the displayed source row, target uniformity row, map row, pulled-back entourage row, transport row, and replay row.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:initial-uniformity-carrier}. A pullback-entourage read begins with a source-pair request in $S$, sends both components through the displayed map row $F$, and then tests the resulting target pair against the target-entourage row $T$.

Use componentwise $\hsame$ transport in $H$ on the source request, the two displayed map reads, and the target-entourage request. These transports preserve the visible coordinates of the packet, so the transported read still lands in the same target-entourage row.

Replay the transported request through $C$. Since $C$ records only the route from source-pair data through $F$ into $T$, the replay reaches the same pulled-back row $E$ and cannot introduce an ambient topology, quotient uniformity, selected representative, or choice coordinate.
\end{proof}

\begin{theorem}[InitialUniformity NameCert obligations]
\label{thm:initial-uniformity-namecert-obligations}
For the carrier of \autoref{def:initial-uniformity-carrier}, the local $\NameCert_{\InitialUniformityUp}$ surface consists exactly of five finite obligations:
\begin{enumerate}
\item carrier exposure for $I=(S,T,F,E,H,C,P,N)$;
\item target-entourage exposure through the target uniformity row $T$;
\item map compatibility requiring every pulled-back request in $E$ to read the displayed map row $F$ before target-entourage testing;
\item pulled-back entourage stability under componentwise $\hsame$ transport and displayed $\Cont$ replay as in \autoref{thm:initial-uniformity-pullback-entourage-stability};
\item refusal of ambient topology on $S$, quotient uniformity, selected representatives, host continuity, open-cover compactness, countable choice, and external completion principles.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier exposure is the projection of the finite tuple $I=(S,T,F,E,H,C,P,N)$. The target-entourage exposure is the projection of $T$, and map compatibility is the requirement that every entry of $E$ is read only after its two source components have been sent through $F$.

The stability obligation is exactly \autoref{thm:initial-uniformity-pullback-entourage-stability}. It binds source-pair transport, target-entourage transport, and continuation replay to the same pulled-back entourage row.

The refusal obligation follows from the carrier inventory. No row stores an ambient topology, quotient uniformity, selected representative family, host continuity theorem, open-cover compactness proof, countable-choice selector, or external completion object, so the local certificate exports only the finite pullback-uniformity route.
\end{proof}

\falsifiablePrediction{Every accepted $\InitialUniformityUp$ pullback-entourage read factors through one source row, one target uniformity row, one displayed map row, one pulled-back entourage row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming.}

\independenceWitness{real-uniform-structure, uniform-entourage-basis, uniform-space-completion: $\InitialUniformityUp$ is not bijective to any listed sibling because it packages the source carrier, target uniformity, displayed map, pulled-back entourage row, transport, replay, provenance, and local NameCert as one pullback-uniformity certificate.}

\closureat{InitialUniformityUp}{seedStr}

\begin{closurestatus}{\InitialUniformityUp}
  \constructivestory{An $\InitialUniformityUp$ packet is generated from a source carrier row, a target uniformity row, a displayed map row, pulled-back entourage rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:initial-uniformity-carrier}, \autoref{thm:initial-uniformity-pullback-entourage-stability}, and \autoref{thm:initial-uniformity-namecert-obligations} seed the finite pullback-uniformity boundary for target-entourage consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient topology, quotient uniformity, selected representatives, host continuity, open-cover compactness, countable choice, external completion, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier exposure, target-entourage exposure, map compatibility, pulled-back entourage stability, transport, replay, provenance, local naming, and nonescape for BEDC.Derived.InitialUniformityUp.}
\end{closurestatus}
