\chapter{A Concrete Naming Certificate for $\PoincareRecurrenceUp$}
\label{ch:concrete-instances-poincare-recurrence-namecert}
\origin{human}

Following Poincare's recurrence theorem and Bishop-style finite evidence, the $\PoincareRecurrenceUp$ packet records the displayed finite return-window route behind recurrence in a measure-preserving system. It sits after the finite routed-flow carrier of \autoref{ch:concrete-instances-dynsystem-namecert}, the invariant-measure surface of \autoref{ch:concrete-instances-ergodic-namecert}, the normalized probability carrier of \autoref{ch:concrete-instances-probspace-namecert}, and the underlying measure packet of \autoref{ch:concrete-instances-measure-namecert}. The packet names only a finite recurrence certificate; it is not a host infinite orbit theorem, not a selected recurrent point, not a sigma-completion principle, and not an ambient ergodic decomposition.

\begin{definition}[Poincare recurrence carrier]
\label{def:poincare-recurrence-carrier}
A $\PoincareRecurrenceUp$ carrier is a finite $\BHist$ packet
$$
R=(D,E,P,M,A,W,T,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the $\DynSystemUp$ finite routed-flow row, exposing the inspected step relation and orbit cells.
\item $E$ is the $\ErgodicUp$ invariant-measure or recurrence-facing row used only as finite classifier support.
\item $P$ is the $\ProbSpaceUp$ normalization row for the total event and event classifier.
\item $M$ is the $\MeasureUp$ measurable-set row naming the inspected positive-measure cell $A$.
\item $A$ is the displayed source event whose nonzero measure is being tested for return.
\item $W$ is the finite return-window row, listing the inspected nonzero times and their displayed inverse-image or forward-image cells.
\item $T$ is the return-hit row asserting that the window contains a measured overlap between $A$ and an allowed return of $A$.
\item $H$ records componentwise $\hsame$ transport for the dynamic, invariant, probability, measure, event, window, return-hit, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay through the dynamic route, event classifier, finite window, and return-hit ledger.
\item $Q$ is the $\Pkg$ provenance over $\PoincareRecurrenceUp$, $\DynSystemUp$, $\ErgodicUp$, $\ProbSpaceUp$, $\MeasureUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PoincareRecurrenceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through these eleven rows. It has no coordinate for a completed measure algebra, infinite orbit selector, countable recurrence schedule, host almost-everywhere predicate, or ergodic decomposition.
\end{definition}

\begin{theorem}[Poincare recurrence NameCert obligations]
\label{thm:poincare-recurrence-namecert-obligations}
For every accepted $\PoincareRecurrenceUp$ carrier
$$
R=(D,E,P,M,A,W,T,H,C,Q,N),
$$
the local $\NameCert_{\PoincareRecurrenceUp}$ surface consists exactly of finite routed dynamics, invariant-measure support, probability normalization, measurable-event exposure, finite return-window data, a displayed return-hit row, componentwise transport, displayed replay, package provenance, and local naming through the rows $D,E,P,M,A,W,T,H,C,Q,N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:poincare-recurrence-carrier}. The rows $D,E,P,M,A$ expose the only dynamic, invariant, probability, measure, and source-event data visible to the packet.

Read the return evidence next. The row $W$ gives the inspected finite return window, and $T$ records the measured overlap that certifies a return within that displayed window.

Finally attach $H,C,Q,N$. Componentwise transport, continuation replay, provenance, and local naming preserve exactly the displayed rows, so the certificate cannot export an infinite orbit selector, a completed measure algebra, a countable recurrence schedule, or an ergodic decomposition.
\end{proof}

\begin{theorem}[Poincare recurrence return-window handoff]
\label{thm:poincare-recurrence-return-window-handoff}
Every accepted $\PoincareRecurrenceUp$ recurrence read factors through the route
$$
D\longmapsto E\longmapsto P\longmapsto M\longmapsto A\longmapsto W\longmapsto T\longmapsto H,C,Q,N
$$
before a downstream consumer receives the return claim. Thus the handoff to later dynamic or probability formalization is a displayed finite system row, invariant-support row, probability normalization row, measurable source event, return-window ledger, return-hit witness, transport, replay, provenance, and local naming data.
\end{theorem}
\begin{proof}
Start with a consumer requesting recurrence data. The packet first exposes the finite dynamic row $D$, the invariant-support row $E$, and the normalized probability row $P$.

The measurable source event is then fixed by $M$ and $A$. No return statement is available before these rows name the event whose positive measure is being inspected.

Only after that does the finite window $W$ feed the return-hit row $T$. The structural rows $H,C,Q,N$ preserve the same route for later consumers, so the handoff is a finite return-window certificate rather than a host recurrence theorem.
\end{proof}

\begin{theorem}[Poincare recurrence measure-preserving nonescape]
\label{thm:poincare-recurrence-measure-preserving-nonescape}
Every accepted $\PoincareRecurrenceUp$ measure-preserving read remains inside the finite carrier of \autoref{def:poincare-recurrence-carrier}. In particular, a consumer can read a recurrence claim only after displaying the $\DynSystemUp$ row, $\ErgodicUp$ invariant-support row, $\ProbSpaceUp$ normalization row, $\MeasureUp$ event row, finite return-window ledger, return-hit row, componentwise $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. No accepted read may replace this route by a selected recurrent point, a completed invariant sigma-algebra, a countable-choice return schedule, a host almost-everywhere predicate, or an ambient ergodic decomposition.
\end{theorem}
\begin{proof}
Let a consumer request a measure-preserving recurrence claim from an accepted carrier. Projection of \autoref{def:poincare-recurrence-carrier} shows that the request first meets $D,E,P,M,A$ and has no independent coordinate for a selected point or completed orbit.

The finite return-window row $W$ is downstream from the displayed measurable source event, and the return-hit row $T$ is downstream from that window. Hence the recurrence read is already tied to a finite inspected window and its measured overlap.

The remaining rows $H,C,Q,N$ add no new analytic primitive. They transport equal displayed histories, replay the finite route, record package provenance, and attach the local name. Therefore every accepted measure-preserving read stays inside the finite recurrence certificate surface and cannot escape to the excluded host principles.
\end{proof}

\falsifiablePrediction{If a recurrence-facing consumer preserves the $\DynSystemUp$ row but drops the $\ProbSpaceUp$ normalization row, the $\MeasureUp$ event row, or the finite return-window row, it is not reading a $\PoincareRecurrenceUp$ packet.}

\independenceWitness{dynsystem, ergodic, probspace, measure: no listed sibling is bijective to $\PoincareRecurrenceUp$ because this packet jointly carries finite routed dynamics, invariant-support provenance, normalized probability, measurable source events, finite return windows, return-hit evidence, transport, replay, package sourcing, and local naming.}

\begin{closurestatus}{\PoincareRecurrenceUp}
  \constructivestory{A $\PoincareRecurrenceUp$ packet is generated from a finite DynSystem route, Ergodic invariant-support row, ProbSpace normalization row, Measure event row, source event, finite return-window ledger, return-hit witness, componentwise hsame transport, Cont replay, Pkg provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:poincare-recurrence-carrier}, \autoref{thm:poincare-recurrence-namecert-obligations}, \autoref{thm:poincare-recurrence-return-window-handoff}, and \autoref{thm:poincare-recurrence-measure-preserving-nonescape} seed the finite recurrence route through dynamics, invariant support, probability normalization, measurable events, return windows, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host recurrence theorems, selected recurrent points, completed invariant sigma-algebras, countable-choice return schedules, almost-everywhere predicates, ergodic decompositions, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, dynamic routing, invariant-support stability, probability normalization, measurable-event exposure, return-window handoff, return-hit nonescape, transport, replay, provenance, and local naming for future BEDC.Derived.PoincareRecurrenceUp.}
\end{closurestatus}
