\chapter{A Concrete Naming Certificate for $\PringsheimConvergenceUp$}
\label{ch:concrete-instances-pringsheim-convergence-namecert}
\origin{human}

Pringsheim and Bishop--Bridges constructive analysis treat convergence over two indices as an explicit route through finite rectangles, cofinal tails, and displayed regular readback, not as an ambient appeal to a completed double limit. The $\PringsheimConvergenceUp$ packet records this route for positive rectangle partial sums after the two-parameter surface of \autoref{ch:concrete-instances-cauchy-double-sequence-namecert}, the iterated handoff of \autoref{ch:concrete-instances-moore-osgood-namecert}, the finite windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}. It is a finite NameCert reconstruction of the Pringsheim route; it does not claim host double-series convergence, quotient equality of arrays, selected sums, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Pringsheim convergence carrier]
\label{def:pringsheim-convergence-carrier}
A $\PringsheimConvergenceUp$ carrier is a finite $\BHist$ packet
$$
K=(X,S,T,M,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the $\CauchyDoubleSequenceUp$ source row. It records the two-parameter array and the finite rectangle requests from which Pringsheim reads are admitted.
\item $S$ is the positive rectangle partial-sum row. It lists the displayed positive rectangular sums, successor-edge additions, and finite positivity witnesses visible to the packet.
\item $T$ is the diagonal and cofinal tail-budget row. It binds each tolerance request to a diagonal entry point and to cofinal rectangle enlargements beyond that entry point.
\item $M$ is the $\MooreOsgoodUp$ handoff row. It records the iterated-limit route available when a consumer asks to compare the Pringsheim rectangle read with an iterated regular read.
\item $W$ is the $\StreamNameUp$ window row. It stores the finite rectangle windows, index bounds, and inspection order used by $X,S,T,M$.
\item $R$ is the $\RegSeqRatUp$ readback row. It reads the same rectangle partial sums and cofinal tail budgets as a regular rational sequence before any endpoint seal is exported.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger. It stores dyadic tolerances, slack radii, denominator bounds, rectangle-side budgets, and accumulated arithmetic error.
\item $E$ is the $\RealUp$ seal row. It is visible only after the source, positive rectangle sums, cofinal tail budget, Moore-Osgood handoff, StreamName windows, RegSeqRat readback, and DyadicRatCore ledger have been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source, rectangle sums, tail budget, handoff, windows, readback, tolerance ledger, real seal, continuation, provenance, and local naming row.
\item $C$ stores displayed $\Cont$ replay from rectangle inspection to positive partial sums, from those sums to cofinal tail budgets, from the budgets to the Moore-Osgood and RegSeqRat handoffs, and from the handoffs to the real seal.
\item $P$ is the $\Pkg$ provenance over $\PringsheimConvergenceUp$, $\CauchyDoubleSequenceUp$, $\MooreOsgoodUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\PringsheimConvergenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $X,S,T,M,W,R,D,E,H,C,P,N$. It has no coordinate for host double-series convergence, quotient equality of arrays, selected infinite sums, countable choice, ambient $\RealUp$ completeness, Lean verification, or a standard bridge.
\end{definition}

\begin{theorem}[Pringsheim convergence NameCert obligations]
\label{thm:pringsheim-convergence-namecert-obligations}
For every accepted $\PringsheimConvergenceUp$ carrier $K=(X,S,T,M,W,R,D,E,H,C,P,N)$, the local $\NameCert_{\PringsheimConvergenceUp}$ surface consists exactly of the following finite obligation rows:
\begin{enumerate}
\item carrier admission for the displayed CauchyDoubleSequence source, positive rectangle partial sums, diagonal and cofinal tail budget, Moore-Osgood handoff, StreamName windows, regular rational readback, dyadic tolerance ledger, real seal, transport, replay, provenance, and local naming row;
\item rectangle-window exactness, requiring every inspected two-index term and every positive rectangle partial sum to pass through $X,S,W$ before a tail request is admitted;
\item cofinal-tail exactness, requiring $T$ to display the diagonal entry point, rectangle enlargement rule, dyadic tolerance request, and cofinal threshold consumed by the Pringsheim route;
\item iterated-limit compatibility, requiring $M$ to expose only the Moore-Osgood handoff already routed through the same windows and tail ledger;
\item $\RegSeqRatUp$ readback, requiring $R$ to read the same positive rectangle sums and cofinal budgets before any $\RealUp$ seal is available;
\item real-seal nonescape, requiring $E$ to remain downstream of $X,S,T,M,W,R,D$ and to export no host double-series convergence, quotient array equality, selected infinite sum, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge datum;
\item componentwise transport, displayed replay, provenance, and local naming for the same route through $H,C,P,N$.
\end{enumerate}
No Pringsheim convergence obligation is stored outside these rows.
\end{theorem}
\begin{proof}
Project the accepted packet $K=(X,S,T,M,W,R,D,E,H,C,P,N)$. The carrier definition exposes exactly the CauchyDoubleSequence source, positive rectangle partial sums, diagonal and cofinal tail budget, Moore-Osgood handoff, StreamName windows, regular readback, dyadic ledger, seal, and structural rows.

The rectangle data are read first. The source row $X$ and window row $W$ supply only displayed finite two-parameter windows, while $S$ supplies only positive rectangle partial sums and their visible successor-edge additions.

The tail and handoff route then passes through $T,M,R,D$. The row $T$ records the diagonal entry point and cofinal enlargement budget, $M$ records the Moore-Osgood comparison surface, $R$ performs the regular rational readback, and $D$ stores the dyadic tolerances consumed by both handoffs.

Finally $E,H,C,P,N$ seal, transport, replay, source, and name the same displayed route. Since no excluded analytic, quotient, choice, verification, or bridge object appears as a carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Pringsheim convergence iterated-limit route]
\label{thm:pringsheim-convergence-iterated-limit-route}
Let $K=(X,S,T,M,W,R,D,E,H,C,P,N)$ be an accepted $\PringsheimConvergenceUp$ carrier. Every $\RegSeqRatUp$ or $\RealUp$ consumer that compares the Pringsheim rectangle read with an iterated-limit read factors through
$$
X,S,W \longmapsto T,D \longmapsto M,R \longmapsto E,H,C,P,N .
$$
Thus the comparison uses the displayed CauchyDoubleSequence source, positive rectangle partial sums, StreamName windows, diagonal and cofinal tail budgets, DyadicRatCore tolerance ledger, Moore-Osgood handoff, RegSeqRat readback, RealUp seal, transport, replay, provenance, and local naming. It cannot be replaced by host double-series convergence, quotient equality of arrays, a selected infinite sum, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with a consumer comparing the Pringsheim rectangle read with an iterated-limit read. By \autoref{def:pringsheim-convergence-carrier}, the only visible two-parameter source data are $X$ and the finite windows $W$, and the only visible rectangle-sum data are the positive partial sums in $S$.

The comparison cannot reach an iterated route before the tail budget is displayed. The diagonal and cofinal row $T$ names the finite entry point and allowed rectangle enlargements, while $D$ accounts for the dyadic tolerances and accumulated arithmetic error.

The Moore-Osgood row $M$ and regular readback row $R$ then expose the comparison surface. Both rows read the same windows and budgets already displayed by $X,S,T,W,D$, so neither row can choose a separate array representative, limiting value, or external completeness principle.

The route reaches a real-facing consumer only through $E$ and is preserved by $H,C,P,N$. Therefore every such comparison factors through the displayed packet route and has no coordinate for the excluded host, quotient, choice, or completeness data.
\end{proof}

\begin{theorem}[Pringsheim convergence real seal nonescape]
\label{thm:pringsheim-convergence-real-seal-nonescape}
In every accepted $\PringsheimConvergenceUp$ carrier, the $\RealUp$ seal row $E$ is downstream of the CauchyDoubleSequence source, positive rectangle partial sums, diagonal and cofinal tail budget, Moore-Osgood handoff, StreamName windows, RegSeqRat readback, and DyadicRatCore tolerance ledger. Consequently a Real-facing consumer cannot obtain from the packet a host double-series convergence theorem, quotient equality of arrays, selected infinite sum, countable choice, ambient $\RealUp$ completeness, Lean verification, or standard bridge.
\end{theorem}
\begin{proof}
Read the carrier order in \autoref{def:pringsheim-convergence-carrier}. The seal row $E$ is exposed only after $X,S,T,M,W,R,D$ have supplied the source, positive rectangle sums, cofinal tail budget, iterated handoff, finite windows, regular readback, and dyadic tolerance data.

Apply \autoref{thm:pringsheim-convergence-namecert-obligations}. The real-seal nonescape clause binds $E$ to that same displayed route, and the transport, replay, provenance, and local naming rows preserve the route without adding any new analytic coordinate.

Thus a Real-facing consumer receives only the sealed endpoint of the finite certificate. There is no row from which the consumer could read host double-series convergence, quotient array equality, a selected infinite sum, choice, ambient completeness, Lean verification, or bridge data.
\end{proof}

\falsifiablePrediction{Every $\PringsheimConvergenceUp$ Real-facing read factors through a CauchyDoubleSequence source, positive rectangle partial sums, StreamName windows, diagonal and cofinal tail budgets, a DyadicRatCore tolerance ledger, Moore-Osgood and RegSeqRat handoffs, a RealUp seal, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{cauchydoublesequence, moore-osgood, streamname, regseqrat, dyadicratcore, real: $\PringsheimConvergenceUp$ is not bijective to any listed sibling because it jointly carries a two-parameter source, positive rectangle partial sums, cofinal tail budgets, iterated-limit handoff, regular readback, dyadic tolerance accounting, real sealing, transport, continuation, provenance, and local naming.}

\closureat{PringsheimConvergenceUp}{seedStr}

\begin{closurestatus}{\PringsheimConvergenceUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:pringsheim-convergence-carrier}, \autoref{thm:pringsheim-convergence-namecert-obligations}, \autoref{thm:pringsheim-convergence-iterated-limit-route}, and \autoref{thm:pringsheim-convergence-real-seal-nonescape} seed the finite constructive Pringsheim two-parameter convergence route from positive rectangle partial sums through cofinal tail budgets to RealUp sealing.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host double-series convergence, quotient equality of arrays, selected infinite sums, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, rectangle-window exactness, cofinal-tail exactness, Moore-Osgood handoff compatibility, RegSeqRat readback, Real seal nonescape, and structural transport for BEDC.Derived.PringsheimConvergenceUp.}
  \constructivestory{A $\PringsheimConvergenceUp$ packet is generated from a CauchyDoubleSequence source, positive rectangle partial sums, a diagonal and cofinal tail-budget row, a Moore-Osgood handoff row, StreamName windows, a RegSeqRat readback row, a DyadicRatCore tolerance ledger, a RealUp seal row, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
