\chapter{A Concrete Naming Certificate for $\NeutralReifierUp$}
\label{ch:concrete-instances-neutral-reifier-namecert}
\origin{human}

The $\NeutralReifierUp$ packet isolates the neutral-reflection and semantic readback component used by normalization-by-evaluation. It realizes the MetaCIC normalization audit route of \autoref{ch:metacic-normalization-audit-map} as finite neutral, semantic-value, readback, transport, replay, provenance, and local NameCert rows, while sitting beside the lambda-calculus certificate of \autoref{ch:concrete-instances-lambdacalc-namecert}, the candidate-mediated strong-normalization packet of \autoref{ch:concrete-instances-metacic-candidate-strong-normalization-namecert}, and the normalization-by-evaluation packet of \autoref{ch:concrete-instances-normalization-by-evaluation-namecert}. The packet names the reifier component only; it does not assert global normalization, unrestricted MetaCIC subject reduction, host evaluator soundness, or quotient equality of terms.

\begin{definition}[NeutralReifier carrier]
\label{def:neutral-reifier-carrier}
A $\NeutralReifierUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,Z,V,U,R,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the typed neutral-term row, recording the context, type, and neutral spine presented to the reifier.
\item $Z$ is the neutral-reflection row, naming variables, eliminator spines, and application heads that may be reflected into semantic values.
\item $V$ is the semantic-value row produced by reflection or by a prior accepted evaluation packet.
\item $U$ is the universe or type-level guard row controlling which readback shape is allowed for the displayed semantic value.
\item $R$ is the readback row that produces a normal neutral or normal form from $Z,V,U$.
\item $A$ is the audit-route row binding the packet to the candidate-mediated MetaCIC normalization route of \autoref{ch:metacic-normalization-audit-map}.
\item $H$ records componentwise $\hsame$ transport for neutral terms, reflection rows, semantic values, type guards, readback rows, audit rows, replay, provenance, and local names.
\item $C$ records displayed $\Cont$ replay from a requested reification read through $T,Z,V,U,R,A$.
\item $P$ is the $\Pkg$ provenance over $\LambdaCalcUp$, $\MetaCICCandidateStrongNormalizationUp$, $\NormalizationByEvaluationUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\NeutralReifierUp}$ row.
\end{enumerate}
The classifier accepts the packet only when neutral reflection and readback remain finite displayed rows tied to the audit route. It has no slot for a host normalizer, a semantic equality oracle, a quotient of terms, or an unconditional strong-normalization theorem.
\end{definition}

\begin{theorem}[NeutralReifier NameCert obligations]
\label{thm:neutral-reifier-namecert-obligations}
For every accepted $\NeutralReifierUp$ carrier $Q=(T,Z,V,U,R,A,H,C,P,N)$, the local $\NameCert_{\NeutralReifierUp}$ surface consists of the following six rows:
\begin{enumerate}
\item carrier admission for neutral terms, neutral reflection, semantic values, type guards, readback, audit-route, transport, replay, provenance, and local naming;
\item neutral reflection, requiring every reflected variable or eliminator spine in $Z$ to be tied to the displayed context and typed neutral term row $T$;
\item semantic value admission, requiring $V$ to arise from reflection or from an accepted evaluation packet named in the provenance row;
\item guarded readback, requiring $R$ to read $Z,V,U$ before producing a normal neutral or normal form;
\item transport and replay stability, requiring componentwise $\hsame$ and displayed $\Cont$ to preserve the same $T,Z,V,U,R,A$ route;
\item audit nonescape, excluding host normalization oracles, semantic equality oracles, quotient syntax equality, unrestricted subject reduction, and evidence-free strong normalization.
\end{enumerate}
No consumer of the packet receives any stronger MetaCIC normalization claim than these rows display.
\end{theorem}
\begin{proof}
Carrier admission is immediate from \autoref{def:neutral-reifier-carrier}. The tuple exposes neutral terms, reflection, semantic values, type guards, readback, the audit route, transport, replay, provenance, and local naming as the only rows.

Neutral reflection is tied to $T$ and $Z$. Variables and eliminator spines are reflected only through the displayed context and typed neutral surface, so the packet cannot create a semantic value without a visible neutral source.

Semantic admission and guarded readback then pass through $V,U,R$. The value row is either reflected from $Z$ or imported through an accepted evaluation packet named by $P$, and the readback row must consume the displayed type guard before producing syntax.

Transport and replay stability use $H$ and $C$. These rows move the same neutral, semantic-value, type-guard, readback, and audit-route coordinates together, preserving the route into \autoref{ch:metacic-normalization-audit-map}.

The audit row $A$, provenance $P$, and local name $N$ keep the packet at the reifier component boundary. Since the carrier has no coordinate for a host normalizer, semantic equality oracle, quotient syntax equality, unrestricted subject reduction, or evidence-free strong normalization, the obligation surface is exactly the six rows listed.
\end{proof}

\falsifiablePrediction{Every accepted $\NeutralReifierUp$ readback factors through the neutral-term row, neutral-reflection row, semantic-value row, type guard, readback row, MetaCIC audit-route row, componentwise transport, continuation replay, provenance, and local $\NameCert$ before any consumer may cite a normal neutral or normal form.}

\independenceWitness{lambdacalc, metacic-candidate-strong-normalization, normalization-by-evaluation: $\NeutralReifierUp$ is not bijective to any listed sibling because it isolates neutral reflection, guarded readback, and MetaCIC audit-route replay as one packet. LambdaCalcUp has beta syntax without semantic reification; MetaCICCandidateStrongNormalizationUp has candidate evidence without reifier rows; NormalizationByEvaluationUp includes full evaluation and substitution stability beyond the neutral reifier component.}

\closureat{NeutralReifierUp}{seedStr}

\begin{closurestatus}{\NeutralReifierUp}
  \constructivestory{A $\NeutralReifierUp$ packet is generated from a typed neutral-term row, neutral-reflection row, semantic-value row, type guard, readback row, MetaCIC audit-route row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:neutral-reifier-carrier} and \autoref{thm:neutral-reifier-namecert-obligations} seed the finite neutral-reflection and readback component for the MetaCIC normalization audit route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close unrestricted MetaCIC normalization, subject reduction, global confluence, semantic equality, quotient syntax equality, host evaluator soundness, or Lean verification.}
  \upgradepath{Obligation closure requires checked carrier admission, neutral reflection, semantic-value admission, guarded readback, transport stability, and audit nonescape for BEDC.Derived.NeutralReifierUp.}
\end{closurestatus}
