\chapter{A Concrete Naming Certificate for $\FiniteIntersectionCompactnessUp$}
\label{ch:concrete-instances-finite-intersection-compactness-namecert}
\origin{human}

Following Bishop and Bridges' constructive compactness practice and Kelley's finite-intersection formulation of compactness, the $\FiniteIntersectionCompactnessUp$ packet records the finite-window compactness data that a completion corridor may inspect without importing a general open-cover theorem. It sits beside the finite-intersection property row of \autoref{ch:concrete-instances-finite-intersection-property-namecert}, the compact metric certificate of \autoref{ch:concrete-instances-compactmetric-namecert}, the closed-interval Cauchy completion row of \autoref{ch:concrete-instances-closed-interval-cauchy-completion-namecert}, the finite epsilon-net row of \autoref{ch:concrete-instances-finite-epsilon-net-namecert}, and the Real seal of \autoref{ch:concrete-instances-real-namecert}. Those neighbors provide the traditional compactness vocabulary; this certificate keeps the usable claim finite, row-displayed, and local to the BEDC NameCert surface.

\begin{definition}[Finite-intersection compactness carrier]
\label{def:finite-intersection-compactness-carrier}
A $\FiniteIntersectionCompactnessUp$ carrier is a finite $\BHist$ packet
$$
F=(I,K,J,E,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite-intersection-property row read from \autoref{ch:concrete-instances-finite-intersection-property-namecert};
\item $K$ is the compact-metric source row read from \autoref{ch:concrete-instances-compactmetric-namecert};
\item $J$ is the closed-interval Cauchy-completion window read from \autoref{ch:concrete-instances-closed-interval-cauchy-completion-namecert};
\item $E$ is the finite epsilon-net witness row read from \autoref{ch:concrete-instances-finite-epsilon-net-namecert};
\item $R$ is the terminal Real-facing seal read from \autoref{ch:concrete-instances-real-namecert};
\item $H$ stores componentwise $\hsame$ transport for finite-intersection rows, compact-metric rows, closed-interval completion windows, finite epsilon-net witnesses, Real seals, provenance, and local naming;
\item $C$ stores displayed $\Cont$ replay for the same finite-window route;
\item $P$ records $\Pkg$ provenance over $\FiniteIntersectionPropertyUp$, $\CompactMetricUp$, $\ClosedIntervalCauchyCompletionUp$, $\FiniteEpsilonNetUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data;
\item $N$ is the local $\NameCert_{\FiniteIntersectionCompactnessUp}$ row.
\end{enumerate}
The carrier records only finite-window compactness data. It contains no coordinate for general open-cover compactness, countable choice, quotient real equality, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Finite-intersection compactness NameCert obligations]
\label{thm:finite-intersection-compactness-namecert-obligations}
For the carrier of \autoref{def:finite-intersection-compactness-carrier}, the local $\NameCert_{\FiniteIntersectionCompactnessUp}$ obligation surface consists exactly of the finite-intersection-property row $I$, compact-metric source row $K$, closed-interval Cauchy-completion window $J$, finite epsilon-net witness row $E$, Real seal row $R$, componentwise transport $H$, continuation replay $C$, provenance $P$, and local naming $N$. A consumer may cite the packet only as finite-window compactness data over those rows.
\end{theorem}
\begin{proof}
Project the carrier tuple $F=(I,K,J,E,R,H,C,P,N)$. The finite-intersection, compact-metric, closed-interval completion, finite epsilon-net, and Real-facing rows are displayed as separate coordinates before any compactness read is available.

Use \autoref{ch:concrete-instances-finite-intersection-property-namecert} for the finite-intersection row and \autoref{ch:concrete-instances-compactmetric-namecert} for the compact-metric source. These rows expose finite compatibility and the metric carrier without producing a general open-cover theorem.

Use \autoref{ch:concrete-instances-closed-interval-cauchy-completion-namecert}, \autoref{ch:concrete-instances-finite-epsilon-net-namecert}, and \autoref{ch:concrete-instances-real-namecert} for the completion window, finite search net, and terminal seal. They keep the read inside finite windows and Real-facing certificates rather than quotient equality or ambient completeness.

The rows $H,C,P,N$ only transport, replay, cite, and name that same finite route. Since no coordinate stores countable choice, trichotomy, quotient real equality, ambient Real completeness, or open-cover compactness, none is exported by the NameCert obligations.
\end{proof}

\closureat{FiniteIntersectionCompactnessUp}{seedStr}

\begin{closurestatus}{\FiniteIntersectionCompactnessUp}
  \constructivestory{A $\FiniteIntersectionCompactnessUp$ packet is generated from finite-intersection-property data, compact-metric source rows, closed-interval Cauchy-completion windows, finite epsilon-net witnesses, Real-facing seals, componentwise transport, continuation replay, provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-intersection-compactness-carrier} and \autoref{thm:finite-intersection-compactness-namecert-obligations} seed finite-window compactness data over finite-intersection, compact-metric, closed-interval completion, finite epsilon-net, and Real-facing rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim general open-cover compactness, countable choice, quotient real equality, trichotomy, ambient Real completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission and finite-window compactness obligations for BEDC.Derived.FiniteIntersectionCompactnessUp.}
\end{closurestatus}
