\chapter{A Concrete Naming Certificate for $\RegularRealCauchySelectorUp$}
\label{ch:concrete-instances-regular-real-cauchy-selector-namecert}
\origin{human}

Following Bishop and Bridges constructive analysis, the $\RegularRealCauchySelectorUp$ packet records the finite selector surface by which an explicit regular-Cauchy Real read exposes its source, modulus, dyadic tolerance ledger, finite windows, regular-rational handoff, and terminal Real seal. It sits after the StreamName windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic arithmetic ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular-rational route of \autoref{ch:concrete-instances-regseqrat-namecert}, the Cauchy-modulus discipline of \autoref{ch:concrete-instances-cauchymodulus-namecert}, and the terminal Real naming surface of \autoref{ch:concrete-instances-real-namecert}. The selector names one displayed read path; it does not choose a quotient-stream representative, select a host Real limit, invoke countable choice, or import ambient Real completeness.

\begin{definition}[Regular Real Cauchy selector carrier]
\label{def:regular-real-cauchy-selector-carrier}
A $\RegularRealCauchySelectorUp$ carrier is a finite $\BHist$ packet
$$
S=(R_0,M,D,W,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R_0$ is the regular Real source row, recording the named Real-facing request before any terminal seal is consumed.
\item $M$ is the explicit $\CauchyModulusUp$ row for the regular-Cauchy read, including the visible request-to-window schedule.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the same modulus request.
\item $W$ is the $\StreamNameUp$ finite-window row selected by $M$ and read against $D$.
\item $Q$ is the $\RegSeqRatUp$ handoff row obtained from the displayed windows and dyadic tolerance data.
\item $E$ is the $\RealUp$ seal row, available only after $R_0,M,D,W,Q$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for the regular source, modulus, dyadic ledger, finite windows, regular-rational handoff, Real seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from the source and modulus rows through dyadic tolerance, finite windows, regular-rational handoff, the Real seal, provenance, and local naming.
\item $P$ is the $\Pkg$ provenance over $\RegularRealCauchySelectorUp$, $\CauchyModulusUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RegularRealCauchySelectorUp}$ row.
\end{enumerate}
The classifier compares accepted selectors only through $R_0,M,D,W,Q,E,H,C,P,N$. It has no coordinate for quotient stream equality, selected representatives, host real equality, countable choice, or ambient completeness of $\RealUp$.
\end{definition}

\begin{theorem}[Regular Real Cauchy selector NameCert obligations]
\label{thm:regular-real-cauchy-selector-namecert-obligations}
For every accepted $\RegularRealCauchySelectorUp$ carrier $S=(R_0,M,D,W,Q,E,H,C,P,N)$, the local $\NameCert_{\RegularRealCauchySelectorUp}$ surface consists exactly of carrier admission for the regular Real source, explicit Cauchy modulus, dyadic tolerance ledger, finite StreamName windows, RegSeqRat handoff, terminal Real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming. Every Real-facing selector read must expose $R_0,M,D,W,Q,H,C,P,N$ before it may consume $E$ as Real seal data.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:regular-real-cauchy-selector-carrier}. The source row is $R_0$, the explicit schedule is $M$, the dyadic tolerance ledger is $D$, the finite observation surface is $W$, and the regular-rational handoff is $Q$.

The certificate orders those rows before the terminal seal. A consumer first reads the regular source and modulus request, then the dyadic tolerance ledger, then the StreamName windows, then the RegSeqRat handoff generated by those displayed rows.

The structural rows $H,C,P,N$ preserve that same route under transport, replay, provenance, and local naming. Since no quotient stream, selected representative, host real equality, countable-choice schedule, or ambient completeness coordinate is present, the listed rows exhaust the local certificate obligations.
\end{proof}

\begin{theorem}[Regular Real Cauchy selector Real seal boundary]
\label{thm:regular-real-cauchy-selector-real-seal}
Any $\RealUp$ consumer of an accepted $\RegularRealCauchySelectorUp$ packet reads the terminal seal only after the regular source, explicit Cauchy modulus, dyadic tolerance ledger, finite StreamName windows, RegSeqRat handoff, transport, replay, provenance, and local naming rows have been displayed. Thus the selector cannot be used as a hidden choice of representative, a host Real limit, a quotient stream equality, or an ambient completeness principle.
\end{theorem}
\begin{proof}
Use \autoref{thm:regular-real-cauchy-selector-namecert-obligations}. It places the Real seal row $E$ downstream of $R_0,M,D,W,Q$ and downstream of the structural rows $H,C,P,N$.

The StreamName and RegSeqRat rows are therefore not optional evidence. They are the visible finite readback through which the explicit Cauchy modulus and dyadic tolerance ledger become Real-facing data.

All excluded objects would require a carrier coordinate absent from \autoref{def:regular-real-cauchy-selector-carrier}. The consumer receives only the displayed selector route, so the Real seal remains a terminal named row rather than a hidden representative, selected limit, quotient equality, or completeness claim.
\end{proof}

\falsifiablePrediction{Every accepted $\RegularRealCauchySelectorUp$ read exposes the regular source row, explicit $\CauchyModulusUp$ row, $\DyadicRatCoreUp$ tolerance ledger, $\StreamNameUp$ finite windows, $\RegSeqRatUp$ handoff, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row before any $\RealUp$ seal is public.}

\independenceWitness{cauchymodulus, dyadicratcore, streamname, regseqrat, real: no listed sibling is bijective with $\RegularRealCauchySelectorUp$ because the packet jointly binds the regular source, explicit modulus, dyadic tolerance ledger, finite windows, regular-rational handoff, terminal Real seal, transport, replay, provenance, and local NameCert.}

\closureat{RegularRealCauchySelectorUp}{seedStr}

\begin{closurestatus}{\RegularRealCauchySelectorUp}
  \constructivestory{A $\RegularRealCauchySelectorUp$ packet is generated from a regular Real source row, explicit Cauchy modulus row, DyadicRatCore tolerance ledger, StreamName finite windows, RegSeqRat handoff, Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:regular-real-cauchy-selector-carrier}, \autoref{thm:regular-real-cauchy-selector-namecert-obligations}, and \autoref{thm:regular-real-cauchy-selector-real-seal} seed the explicit regular-Cauchy Real selector surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close quotient stream equality, selected representatives, selected Real limits, countable choice, ambient Real completeness, Lean verification, or bridge checking for $\RegularRealCauchySelectorUp$.}
  \upgradepath{Obligation closure requires checked carrier admission, explicit modulus exactness, dyadic tolerance stability, StreamName window readback, RegSeqRat handoff, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.RegularRealCauchySelectorUp.}
\end{closurestatus}
