\chapter{A Concrete Naming Certificate for $\LocatedUpperSemicontinuousEnvelopeUp$}
\label{ch:concrete-instances-located-upper-semicontinuous-envelope-namecert}
\origin{human}

Following Bishop and Bridges on constructive real analysis, the
$\LocatedUpperSemicontinuousEnvelopeUp$ packet records the finite envelope
surface by which an upper-semicontinuous majorant is read through located
real windows before any Real-facing consumer inspects a seal. It sits beside
the lower-semicontinuous packet of
\autoref{ch:concrete-instances-lowersemicontinuous-namecert}, the one-sided
$\UpperRealUp$ ledger, the located endpoint discipline of
\autoref{ch:concrete-instances-locatedreal-namecert}, the finite
$\StreamNameUp$ window surface of
\autoref{ch:concrete-instances-streamname-namecert}, the regular rational
readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the
terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}.
The packet names a displayed located upper envelope; it is not a host
limsup, quotient equality of real names, a choice-selected representative, or
an ambient completeness principle.

\begin{definition}[Located upper-semicontinuous envelope carrier]
\label{def:located-upper-semicontinuous-envelope-carrier}
A $\LocatedUpperSemicontinuousEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(L,U,A,W,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L$ is the source $\LowerSemicontinuousUp$ row whose lower-side
sublevel and epigraph windows are being enveloped.
\item $U$ is the $\UpperRealUp$ majorant ledger, recording the upper real
cut rows and their finite comparison requests.
\item $A$ is the located-approximation row, requiring every accepted upper
bound request to be accompanied by a displayed $\LocatedRealUp$ comparison
window.
\item $W$ is the $\StreamNameUp$ row listing the finite windows inspected for
the source, the upper ledger, and the located approximation.
\item $R$ is the $\RegSeqRatUp$ readback row reached after the windows have
been displayed.
\item $Q$ is the terminal $\RealUp$ seal row for the envelope value, visible
only after $L,U,A,W,R$ have been read.
\item $H$ records componentwise $\hsame$ transport for the source,
upper-ledger, located-approximation, window, readback, seal, replay,
provenance, and naming rows.
\item $C$ records displayed $\Cont$ replay from any envelope request through
the same rows.
\item $P$ is the $\Pkg$ provenance over
$\LocatedUpperSemicontinuousEnvelopeUp$, $\LowerSemicontinuousUp$,
$\UpperRealUp$, $\LocatedRealUp$, $\StreamNameUp$, $\RegSeqRatUp$,
$\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\LocatedUpperSemicontinuousEnvelopeUp}$
row.
\end{enumerate}
The carrier has no coordinate for a host limsup, a completed supremum
operator, quotient equality of real names, countable choice, or ambient
$\RealUp$ completeness.
\end{definition}

\begin{theorem}[Located upper-semicontinuous envelope obligation surface]
\label{thm:located-upper-semicontinuous-envelope-obligation-surface}
For every accepted $\LocatedUpperSemicontinuousEnvelopeUp$ carrier
$E=(L,U,A,W,R,Q,H,C,P,N)$, the local
$\NameCert_{\LocatedUpperSemicontinuousEnvelopeUp}$ surface consists exactly
of carrier admission, lower-semicontinuous source exposure, upper-real
majorant exactness, located-comparison routing, finite window readback,
regular rational repacking, terminal Real sealing, componentwise $\hsame$
transport, displayed $\Cont$ replay, provenance, and local naming for the
same finite packet.
\end{theorem}
\begin{proof}
Project the carrier of
\autoref{def:located-upper-semicontinuous-envelope-carrier}. Its analytic
rows are exactly $L,U,A,W,R,Q$, and its structural rows are exactly
$H,C,P,N$.

The source and majorant obligations are read through $L$ and $U$. The row
$L$ exposes only the displayed $\LowerSemicontinuousUp$ surface, while $U$
records the one-sided $\UpperRealUp$ comparison ledger used by the envelope.

The located and Real-facing obligations are $A,W,R,Q$. They force every
upper bound request through a $\LocatedRealUp$ comparison window, a finite
$\StreamNameUp$ inspection, a $\RegSeqRatUp$ readback, and only then the
terminal $\RealUp$ seal.

Finally $H,C,P,N$ transport, replay, source, and name the same finite route.
Since the refused host objects are absent from the carrier, the listed rows
exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Located upper-semicontinuous envelope Real seal boundary]
\label{thm:located-upper-semicontinuous-envelope-real-seal-boundary}
Every $\RealUp$ consumer of an accepted
$\LocatedUpperSemicontinuousEnvelopeUp$ packet reads the terminal envelope
seal only through
$$
\LowerSemicontinuousUp,\UpperRealUp,\LocatedRealUp,\StreamNameUp,\RegSeqRatUp
\longmapsto \RealUp.
$$
Thus the envelope may expose a located upper-semicontinuous Real-facing row,
but it does not export a host limsup, a quotient equality principle, a
choice-selected representative, or ambient Real completeness.
\end{theorem}
\begin{proof}
Begin with a consumer of the terminal row $Q$. By the carrier definition,
there is no route to $Q$ before the lower-semicontinuous source row $L$, the
upper-real majorant ledger $U$, and the located comparison row $A$ have been
displayed.

The finite observation route then passes through the window row $W$ and the
regular rational readback row $R$. These rows make the envelope request a
displayed finite packet rather than a semantic appeal to a completed
upper envelope.

The transport, replay, provenance, and local naming rows preserve that same
route. Hence every Real-seal read is bounded by the displayed
$L,U,A,W,R,Q,H,C,P,N$ coordinates and cannot bypass them through a host
limsup, quotient equality, choice, or ambient completeness.
\end{proof}

\falsifiablePrediction{Every $\LocatedUpperSemicontinuousEnvelopeUp$
Real-facing read factors through displayed $\LowerSemicontinuousUp$,
$\UpperRealUp$, $\LocatedRealUp$, $\StreamNameUp$, $\RegSeqRatUp$,
$\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.}

\independenceWitness{lowersemicontinuous, locatedreal, streamname, regseqrat, real: $\LocatedUpperSemicontinuousEnvelopeUp$ is not bijective to any listed sibling because it jointly carries a lower-semicontinuous source, an upper-real majorant ledger, located comparison windows, regular rational readback, a Real seal, transport, replay, provenance, and local naming.}

\closureat{LocatedUpperSemicontinuousEnvelopeUp}{seedStr}

\begin{closurestatus}{\LocatedUpperSemicontinuousEnvelopeUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-upper-semicontinuous-envelope-carrier}, \autoref{thm:located-upper-semicontinuous-envelope-obligation-surface}, and \autoref{thm:located-upper-semicontinuous-envelope-real-seal-boundary} seed the finite located upper-envelope route from lower-semicontinuous source data through upper-real and located-real comparison windows to a terminal Real seal.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host limsup construction, quotient equality of real names, selected envelope representatives, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, upper-real majorant exactness, located-comparison routing, finite-window readback, regular rational repacking, Real seal descent, transport, replay, provenance, and local naming for BEDC.Derived.LocatedUpperSemicontinuousEnvelopeUp.}
  \constructivestory{A $\LocatedUpperSemicontinuousEnvelopeUp$ packet is generated from a LowerSemicontinuous source row, an UpperReal majorant ledger, LocatedReal comparison windows, StreamName finite observations, RegSeqRat readback, a Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
