\chapter{A Concrete Naming Certificate for $\CauchyTailSupremumUp$}
\label{ch:concrete-instances-cauchy-tail-supremum-namecert}
\origin{human}

Following Bishop and Bridges, the $\CauchyTailSupremumUp$ packet records the finite BEDC surface by which a supremum-bound read of a Cauchy tail is consumed after the displayed tail-bound, threshold, window, dyadic, regular-readback, and real-seal rows are already visible. It sits after the tail-bound certificate of \autoref{ch:concrete-instances-cauchy-tail-bound-namecert}, the threshold discipline of \autoref{ch:concrete-instances-realcauchymodulus-namecert}, the finite stream window of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names a bounded-tail consumer surface; it does not assert an ambient completeness principle, an arbitrary host supremum, or a selected limit of a Cauchy stream.

\begin{definition}[Cauchy tail supremum carrier]
\label{def:cauchy-tail-supremum-carrier}
A $\CauchyTailSupremumUp$ carrier is a finite $\BHist$ packet
$$
S=(B,M,W,D,R,E,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the $\CauchyTailBoundUp$ source row, recording the accepted tail-bound packet from which the bounded-tail read starts.
\item $M$ is the $\RealCauchyModulusUp$ threshold row, naming the stage after which the tail is read.
\item $W$ is the $\StreamNameUp$ tail-window row, listing the inspected tail positions and the finite requests attached to them.
\item $D$ is the $\DyadicRatCoreUp$ upper-bound ledger, recording the dyadic radius, slack comparison, and upper-bound cells used by the supremum-bound read.
\item $R$ is the $\RegSeqRatUp$ readback row obtained from the displayed window and dyadic ledger.
\item $E$ is the $\RealUp$ seal row visible only after the tail-bound source, threshold, window, dyadic ledger, and regular readback have been displayed.
\item $U$ is the supremum-bound row, recording the finite assertion that the displayed upper-bound ledger bounds every inspected tail read admitted by $B,M,W,D,R,E$.
\item $H$ records componentwise $\hsame$ transport for the tail-bound source, threshold, window, dyadic ledger, readback, Real seal, supremum-bound row, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay of the route
$$
B,M,W,D \longmapsto R \longmapsto E \longmapsto U .
$$
\item $P$ is the $\Pkg$ provenance over $\CauchyTailSupremumUp$, $\CauchyTailBoundUp$, $\RealCauchyModulusUp$, $\RegularCauchyCriterionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CauchyTailSupremumUp}$ row.
\end{enumerate}
Accepted carriers are compared only through $B,M,W,D,R,E,U,H,C,P,N$. There is no coordinate for a host supremum operator, quotient stream equality, selected limit, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.
\end{definition}

\begin{theorem}[Cauchy tail supremum NameCert obligations]
\label{thm:cauchy-tail-supremum-namecert-obligations}
For every accepted $\CauchyTailSupremumUp$ carrier
$$
S=(B,M,W,D,R,E,U,H,C,P,N),
$$
the local $\NameCert_{\CauchyTailSupremumUp}$ surface consists exactly of carrier admission for the displayed rows, $\CauchyTailBoundUp$ source exposure through $B$, $\RealCauchyModulusUp$ threshold exposure through $M$, $\StreamNameUp$ tail-window exactness through $W$, $\DyadicRatCoreUp$ upper-bound accounting through $D$, $\RegSeqRatUp$ readback through $R$, $\RealUp$ seal descent through $E$, supremum-bound accountability through $U$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cauchy-tail-supremum-carrier}. The accepted packet exposes exactly $B,M,W,D,R,E,U,H,C,P,N$.

The source and threshold obligations are $B$ and $M$. A consumer first reads the accepted $\CauchyTailBoundUp$ source and then the $\RealCauchyModulusUp$ threshold that restricts which tail positions may be inspected.

The finite readback obligations are $W,D,R,E$. The window row lists the visible tail positions, the dyadic ledger records the upper-bound cells and slack comparison, the regular readback packages those observations, and the Real seal is downstream of those displayed rows.

The supremum-bound obligation is $U$. It records only the finite upper-bound assertion over the admitted tail-window reads, while $H,C,P,N$ transport, replay, source, and name the same packet. Since no excluded principle is a carrier coordinate, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Cauchy tail supremum Real boundary]
\label{thm:cauchy-tail-supremum-real-boundary}
Every $\RealUp$ or completion-facing consumer of an accepted $\CauchyTailSupremumUp$ carrier must read the supremum-bound row only through the finite route
$$
\CauchyTailBoundUp,\RealCauchyModulusUp,\StreamNameUp,\DyadicRatCoreUp
\longmapsto
\RegSeqRatUp
\longmapsto
\RealUp
\longmapsto
\CauchyTailSupremumUp .
$$
Thus the packet supplies a displayed upper bound for admitted Cauchy-tail reads, but it supplies no host supremum, quotient stream equality, selected limit, countable-choice schedule, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge credential.
\end{theorem}
\begin{proof}
Begin with an accepted carrier $S=(B,M,W,D,R,E,U,H,C,P,N)$. Projection gives the tail-bound source, threshold row, finite tail window, dyadic upper-bound ledger, regular readback, Real seal, and supremum-bound row.

The route to $U$ is downstream of $B,M,W,D,R,E$. A consumer cannot read the supremum-bound row until the tail-bound source and threshold have admitted the inspected window and the dyadic ledger has recorded the upper-bound cells consumed by the regular readback.

The Real-facing boundary is the seal row $E$, and it is already downstream of the finite tail route. Componentwise $\hsame$ transport and displayed $\Cont$ replay preserve that order, while $\Pkg$ provenance and the local $\NameCert$ row only source and name the same data.

Therefore the exported object is the finite supremum-bound packet itself. No coordinate remains from which a host supremum, quotient stream equality, selected limit, countable-choice schedule, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge credential could be read.
\end{proof}

\closureat{CauchyTailSupremumUp}{seedStr}

\begin{closurestatus}{\CauchyTailSupremumUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cauchy-tail-supremum-carrier}, \autoref{thm:cauchy-tail-supremum-namecert-obligations}, and \autoref{thm:cauchy-tail-supremum-real-boundary} seed the finite supremum-bound route for Cauchy-tail reads over displayed tail-bound, threshold, window, dyadic, readback, and Real-seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host supremum, quotient streams, selected limits, countable choice, trichotomy, open-cover compactness, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, CauchyTailBound source exposure, modulus-threshold exposure, StreamName tail-window exactness, DyadicRatCore upper-bound accounting, RegSeqRat readback, Real seal descent, supremum-bound accountability, transport, replay, provenance, and local naming for BEDC.Derived.CauchyTailSupremumUp.}
  \constructivestory{A $\CauchyTailSupremumUp$ packet is generated from a CauchyTailBound source row, a RealCauchyModulus threshold row, StreamName tail-window rows, a DyadicRatCore upper-bound ledger, RegSeqRat readback, a RealUp seal, a supremum-bound row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
