\chapter{A Concrete Naming Certificate for $\JordanDecompositionBoundedVariationUp$}
\label{ch:concrete-instances-jordan-decomposition-bounded-variation-namecert}
\origin{human}

Following Jordan's theorem for functions of bounded variation, the $\JordanDecompositionBoundedVariationUp$ packet records the finite BEDC surface by which a bounded-variation real function is read as the difference of two increasing variation ledgers before any Riemann--Stieltjes or Real-facing consumer sees the result. It sits after the bounded-variation carrier of \autoref{ch:concrete-instances-boundedvariation-namecert}, the finite partition-sum ledger of \autoref{ch:concrete-instances-finite-variation-ledger-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic edge-observation route of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal Real seal of \autoref{ch:concrete-instances-real-namecert}. The packet is a displayed Jordan split over finite partition rows; it does not introduce a host function quotient, a selected total-variation supremum, a measure-valued derivative, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Jordan decomposition bounded-variation carrier]
\label{def:jordan-decomposition-bounded-variation-carrier}
A $\JordanDecompositionBoundedVariationUp$ carrier is a finite $\BHist$ packet
$$
J=(B,L,P_{+},P_{-},M,R,D,E,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the accepted $\BoundedVariationUp$ source row.
\item $L$ is the finite $\FiniteVariationLedgerUp$ partition-sum row attached to the same interval and endpoint data.
\item $P_{+}$ records the positive-edge accumulated ledger over the displayed partition.
\item $P_{-}$ records the negative-edge accumulated ledger over the displayed partition.
\item $M$ is the monotonicity witness row for the two accumulated ledgers on common refinements.
\item $R$ is the $\RegSeqRatUp$ readback row for the endpoint and accumulated-value windows.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row for edge signs, absolute-value reads, and common-refinement comparisons.
\item $E$ is the terminal $\RealUp$ seal row reached only after $B,L,P_{+},P_{-},M,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for all source, split, readback, tolerance, Real-seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a bounded-variation request through finite partitions, signed edge ledgers, monotone accumulated rows, rational readback, dyadic tolerance, and terminal Real sealing.
\item $Q$ is the $\Pkg$ provenance over $\JordanDecompositionBoundedVariationUp$, $\BoundedVariationUp$, $\FiniteVariationLedgerUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\JordanDecompositionBoundedVariationUp}$ row.
\end{enumerate}
Accepted packets are compared only through these displayed rows.
\end{definition}

\begin{theorem}[Jordan decomposition bounded-variation NameCert obligations]
\label{thm:jordan-decomposition-bounded-variation-namecert-obligations}
For every accepted $\JordanDecompositionBoundedVariationUp$ carrier $J=(B,L,P_{+},P_{-},M,R,D,E,H,C,Q,N)$, the local $\NameCert_{\JordanDecompositionBoundedVariationUp}$ surface consists exactly of bounded-variation source admission, finite variation-ledger exposure, positive-edge and negative-edge accumulated ledgers, monotonicity on common refinements, RegSeqRat readback, DyadicRatCore tolerance accounting, Real seal exposure, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:jordan-decomposition-bounded-variation-carrier}. The source and partition data are precisely $B$ and $L$, and the two signed accumulated ledgers are $P_{+}$ and $P_{-}$.

The Jordan split is finite at every read. Edge signs and absolute-value comparisons are opened through $D$, accumulated over the displayed partition in $P_{+}$ and $P_{-}$, and checked on common refinements by $M$.

The readback and sealing rows are downstream. The row $R$ exposes regular rational windows for endpoint and accumulated-value reads, and $E$ seals only the Real-facing boundary reached from those finite rows.

Finally $H,C,Q,N$ transport, replay, source, and name the same packet. Since no row stores a host function quotient, a selected global supremum, a measure derivative, countable choice, or ambient Real completeness, none of those objects is exported by the local NameCert surface.
\end{proof}

\begin{theorem}[Jordan decomposition bounded-variation consumer route]
\label{thm:jordan-decomposition-bounded-variation-consumer-route}
Every Riemann--Stieltjes, bounded-variation, or Real-facing consumer of an accepted $\JordanDecompositionBoundedVariationUp$ packet must first read the route
$$
\BoundedVariationUp,\ \FiniteVariationLedgerUp,\ P_{+},\ P_{-},\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp \longmapsto H,C,Q,N .
$$
Thus the difference-of-increasing-functions handoff is exposed as signed finite variation ledgers over common refinements, not as a host-level decomposition of quotient functions or a selected supremum over all partitions.
\end{theorem}
\begin{proof}
Apply \autoref{thm:jordan-decomposition-bounded-variation-namecert-obligations}. A consumer cannot read the positive and negative accumulated ledgers until the bounded-variation source, finite partition ledger, edge signs, and common-refinement row have been displayed.

The handoff to analysis consumers then passes through the rational and Real boundary. The $\RegSeqRatUp$ row $R$ records endpoint and accumulated-value windows, the $\DyadicRatCoreUp$ row $D$ records the tolerance and edge-comparison ledger, and the $\RealUp$ row $E$ seals only the displayed result.

The structural rows $H,C,Q,N$ preserve that route for downstream Riemann--Stieltjes and bounded-variation readers. They add no host function extensionality, quotient-function equality, selected limiting partition, countable choice, or ambient Real-completeness coordinate.
\end{proof}

\falsifiablePrediction{A purported $\JordanDecompositionBoundedVariationUp$ consumer that reads a positive or negative monotone component while omitting the bounded-variation source row, finite variation ledger, signed edge rows, RegSeqRat readback, DyadicRatCore tolerance, Real seal, transport, replay, provenance, or local naming row refutes the packet.}

\independenceWitness{boundedvariation, finite-variation-ledger, regseqrat, dyadicratcore, real: $\JordanDecompositionBoundedVariationUp$ is not bijective with any listed sibling because it joins the bounded-variation source, signed finite partition ledgers, monotone refinement rows, rational readback, dyadic tolerance, Real sealing, transport, replay, provenance, and local naming as one decomposition packet.}

\closureat{JordanDecompositionBoundedVariationUp}{seedStr}

\begin{closurestatus}{\JordanDecompositionBoundedVariationUp}
  \constructivestory{A $\JordanDecompositionBoundedVariationUp$ packet is generated from a BoundedVariationUp source row, a FiniteVariationLedgerUp partition-sum row, positive and negative signed edge ledgers, common-refinement monotonicity rows, RegSeqRat readback, DyadicRatCore tolerance accounting, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:jordan-decomposition-bounded-variation-carrier}, \autoref{thm:jordan-decomposition-bounded-variation-namecert-obligations}, and \autoref{thm:jordan-decomposition-bounded-variation-consumer-route} seed the finite Jordan decomposition route for bounded-variation functions and Riemann--Stieltjes consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, host function quotients, selected total-variation suprema, measure-valued derivatives, countable choice, ambient $\RealUp$ completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, signed finite-ledger exposure, monotonicity on common refinements, RegSeqRat readback, DyadicRatCore tolerance accounting, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.JordanDecompositionBoundedVariationUp.}
\end{closurestatus}
