\chapter{A Concrete Naming Certificate for $\FiniteOscillationRadiusLedgerUp$}
\label{ch:concrete-instances-finite-oscillation-radius-ledger-namecert}
\origin{human}

Following the finite-cover proof of Heine--Cantor in \autoref{ch:visions-compact-uniform-continuity}, the $\FiniteOscillationRadiusLedgerUp$ packet records the compact-cover radius and dyadic oscillation ledger consumed before a uniform-continuity handoff is exposed. It sits beside the compact finite-window route of \autoref{ch:concrete-instances-compact-uniform-oscillation-window-namecert}, the compact oscillation packet of \autoref{ch:concrete-instances-compact-uniform-oscillation-namecert}, the finite lower-bound fold of \autoref{ch:concrete-instances-finite-lower-bound-fold-namecert}, and the uniform modulus consumer of \autoref{ch:concrete-instances-uniformmodulus-namecert}. The packet is finite radius data over displayed covers and oscillation rows; it does not assert open-cover compactness, a selected Lebesgue number outside the ledger, quotient map equality, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Finite oscillation-radius ledger carrier]
\label{def:finite-oscillation-radius-ledger-carrier}
A $\FiniteOscillationRadiusLedgerUp$ carrier is a finite $\BHist$ packet
$$
O=(K,U,A,F,B,W,R,D,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the compact finite-cover or finite-net source row.
\item $U$ is the $\UniformModulusUp$ consumer row receiving the final tolerance-only radius handoff.
\item $A$ records the displayed center-radius cover cells and their rational lower-bound candidates.
\item $F$ is the finite lower-bound fold row over those candidate radii.
\item $B$ is the dyadic oscillation-bound row attached to each displayed cover cell.
\item $W$ is the $\StreamNameUp$ finite-window row for source and target observations.
\item $R$ is the $\RegSeqRatUp$ readback row for those observations.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row for oscillation and radius comparisons.
\item $S$ is the terminal $\RealUp$ seal row reached only after $K,U,A,F,B,W,R,D$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for all cover, fold, oscillation, readback, tolerance, seal, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay from a compact-cover request through radius candidates, finite lower-bound folding, dyadic oscillation checks, uniform-modulus handoff, and terminal Real sealing.
\item $P$ is the $\Pkg$ provenance over $\FiniteOscillationRadiusLedgerUp$, $\UniformModulusUp$, $\FiniteLowerBoundFoldUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteOscillationRadiusLedgerUp}$ row.
\end{enumerate}
Accepted packets are compared only through the displayed finite cover, radius, fold, oscillation, readback, tolerance, seal, transport, replay, provenance, and naming rows.
\end{definition}
\leanchecked{BEDC.Derived.FiniteOscillationRadiusLedgerUp.FiniteOscillationRadiusLedgerTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite oscillation-radius ledger NameCert obligations]
\label{thm:finite-oscillation-radius-ledger-namecert-obligations}
For every accepted $\FiniteOscillationRadiusLedgerUp$ carrier $O=(K,U,A,F,B,W,R,D,S,H,C,P,N)$, the local $\NameCert_{\FiniteOscillationRadiusLedgerUp}$ surface consists exactly of compact finite-cover exposure, uniform-modulus consumer exposure, displayed center-radius candidates, finite lower-bound folding, dyadic oscillation bounds, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance accounting, Real sealing, componentwise transport, displayed replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-oscillation-radius-ledger-carrier}. The compact-cover source and uniform-modulus consumer are $K$ and $U$, while $A,F,B$ supply the finite radius and oscillation ledger.

The radius handoff is finite. Candidate radii are listed in $A$, folded in $F$, and checked against the displayed dyadic oscillation row $B$ before any downstream modulus row is read.

The readback remains on the same route. Rows $W,R,D,S$ expose finite observations, regular rational windows, dyadic tolerance comparisons, and the terminal Real seal after the radius ledger has been displayed.

Finally $H,C,P,N$ transport, replay, source, and name the same packet. Since no row stores open-cover compactness, an external Lebesgue-number selector, quotient map equality, countable choice, or ambient Real completeness, the local NameCert surface cannot export those objects.
\end{proof}

\begin{theorem}[Finite oscillation-radius ledger uniform handoff]
\label{thm:finite-oscillation-radius-ledger-uniform-handoff}
Every compact-uniform-continuity consumer of an accepted $\FiniteOscillationRadiusLedgerUp$ packet must read compact finite-cover rows, center-radius candidates, the finite lower-bound fold, dyadic oscillation bounds, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, and the terminal Real seal before it consumes the $\UniformModulusUp$ handoff. The handoff is a finite ledger route, not an open-cover compactness theorem or a selected radius outside the packet.
\end{theorem}
\begin{proof}
Apply \autoref{thm:finite-oscillation-radius-ledger-namecert-obligations}. The compact-cover row, radius candidates, lower-bound fold, and dyadic oscillation row are all displayed before the uniform-modulus consumer may read the handoff.

The finite readback rows keep the same route visible. A consumer reaches $W,R,D,S$ only after the cover and oscillation ledger has fixed the radius row, so the final Real-facing seal cannot replace the finite ledger by a host compactness or completeness argument.

The structural rows $H,C,P,N$ preserve the same compact-cover and oscillation-radius path. They add no selected Lebesgue number outside the ledger, quotient map equality, countable choice, or ambient Real-completeness coordinate.
\end{proof}

\falsifiablePrediction{Every accepted $\FiniteOscillationRadiusLedgerUp$ reader that claims a uniform-modulus handoff while omitting compact finite-cover exposure, center-radius candidates, finite lower-bound folding, dyadic oscillation bounds, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance, Real sealing, hsame transport, Cont replay, Pkg provenance, or local naming refutes the packet.}

\independenceWitness{compact-uniform-oscillation-window, compact-uniform-oscillation, finite-lower-bound-fold, uniformmodulus, streamname, regseqrat, dyadicratcore, real: $\FiniteOscillationRadiusLedgerUp$ is not bijective with any listed sibling because it joins compact-cover radius candidates, dyadic oscillation checks, finite lower-bound folding, uniform-modulus handoff, readback, tolerance, Real sealing, transport, replay, provenance, and local naming as one ledger.}

\closureat{FiniteOscillationRadiusLedgerUp}{seedStr}

\begin{closurestatus}{\FiniteOscillationRadiusLedgerUp}
  \constructivestory{A $\FiniteOscillationRadiusLedgerUp$ packet is generated from compact finite-cover rows, UniformModulusUp consumer rows, displayed center-radius candidates, a FiniteLowerBoundFoldUp row, dyadic oscillation bounds, StreamName windows, RegSeqRat readback, DyadicRatCore tolerance accounting, a RealUp seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-oscillation-radius-ledger-carrier}, \autoref{thm:finite-oscillation-radius-ledger-namecert-obligations}, and \autoref{thm:finite-oscillation-radius-ledger-uniform-handoff} seed the compact-cover radius, dyadic oscillation, and uniform-continuity handoff route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, open-cover compactness, selected Lebesgue numbers outside the packet, quotient map equality, countable choice, ambient $\RealUp$ completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, compact finite-cover exposure, radius-candidate exposure, finite lower-bound folding, dyadic oscillation accounting, uniform-modulus handoff, finite readback, tolerance accounting, Real seal nonescape, transport, replay, provenance, and local naming for BEDC.Derived.FiniteOscillationRadiusLedgerUp.}
\end{closurestatus}
