\chapter{A Concrete Naming Certificate for $\FiniteFourierEnergyUp$}
\label{ch:concrete-instances-finite-fourier-energy-namecert}
\origin{human}

Following Parseval and Plancherel's finite-energy route in Fourier analysis, the $\FiniteFourierEnergyUp$ packet records the finite energy certificate that can be read between the Fourier observation surface of \autoref{ch:concrete-instances-fourier-namecert} and the Parseval identity surface of \autoref{ch:concrete-instances-parseval-namecert}. It consumes circle source rows, inner-product pairing rows, integral energy rows, rational readback rows, dyadic tolerance rows, and terminal Real seals without claiming an ambient Plancherel theorem, inversion theorem, completed Hilbert space, or quotient coefficient object.

\begin{definition}[Finite Fourier energy carrier]
\label{def:finite-fourier-energy-carrier}
A $\FiniteFourierEnergyUp$ carrier is a finite $\BHist$ packet
$$
E=(F,V,S,I,J,Q,D,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the $\FourierUp$ finite observation row, listing the sampled modes, coefficient probes, transform-window probes, and truncation bounds under inspection.
\item $V$ is the $\ParsevalUp$ finite identity row, recording the coefficient-energy ledger and matching integral-energy ledger already displayed by the Parseval packet.
\item $S$ is the circle source row, exposing only the finite phase samples and source classifier data consumed by the Fourier probes.
\item $I$ is the $\InnerProductUp$ pairing row for the coefficient and source rows.
\item $J$ is the $\IntegralUp$ energy row that reads the same finite source window as an integral-energy observation.
\item $Q$ is the rational-readback row, using $\RegSeqRatUp$ data for finite sums, pairings, integral observations, and displayed energy comparisons.
\item $D$ is the $\DyadicRatCoreUp$ tolerance row for summation, pairing, integral readback, Parseval comparison, and downstream energy-window reuse.
\item $R$ is the $\RealUp$ seal row reached only after the Fourier, Parseval, circle, inner-product, integral, rational-readback, and dyadic-tolerance rows have been displayed.
\item $H$ stores componentwise $\hsame$ transport for all displayed rows.
\item $C$ records the displayed $\Cont$ replay route from Fourier coefficient windows through Parseval energy comparison and into the Real seal.
\item $P$ is the $\Pkg$ provenance over $\FiniteFourierEnergyUp$, $\FourierUp$, $\ParsevalUp$, $\SOneUp$, $\InnerProductUp$, $\IntegralUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\FiniteFourierEnergyUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $F,V,S,I,J,Q,D,R,H,C,P,N$. It has no coordinate for ambient Plancherel, Fourier inversion, completed Hilbert-space norm equality, host function equality, selected representatives, or quotient coefficient classes.
\end{definition}

\begin{theorem}[Finite Fourier energy NameCert obligations]
\label{thm:finite-fourier-energy-namecert-obligations}
For every accepted $\FiniteFourierEnergyUp$ carrier $E=(F,V,S,I,J,Q,D,R,H,C,P,N)$, the local $\NameCert_{\FiniteFourierEnergyUp}$ surface consists exactly of carrier admission for the displayed Fourier, Parseval, circle, inner-product, integral, rational-readback, dyadic-tolerance, Real-seal, transport, replay, provenance, and local naming rows; coefficient-window exactness through $F$; Parseval-row attachment through $V$; source and pairing exposure through $S,I$; integral-energy exposure through $J$; rational and dyadic accounting through $Q,D$; Real-seal non-escape through $R$; and componentwise transport, displayed replay, package provenance, and local naming through $H,C,P,N$.
\end{theorem}
\begin{proof}
Project the carrier in \autoref{def:finite-fourier-energy-carrier}. The finite inventory is exactly $F,V,S,I,J,Q,D,R,H,C,P,N$, so the NameCert obligations cannot cite a hidden analytic coordinate.

The energy-facing rows are read in order. The Fourier row $F$ supplies the finite coefficient and transform windows, the Parseval row $V$ supplies the finite energy identity surface, the circle row $S$ supplies the finite source samples, and the pairing and integral rows $I,J$ expose the two sides of the energy comparison.

The numerical endpoint is also finite. Rational readback $Q$ and dyadic tolerance $D$ record the visible arithmetic data before the Real seal $R$ is reached.

Finally $H,C,P,N$ transport, replay, source, and name the same route. Since the carrier has no Plancherel, inversion, completed norm, host equality, representative-selection, or quotient coordinate, none of those conclusions can be projected from the packet.
\end{proof}

\begin{theorem}[Finite Fourier energy Parseval route]
\label{thm:finite-fourier-energy-parseval-route}
Every consumer read of a $\FiniteFourierEnergyUp$ packet factors through the finite Fourier observation surface of \autoref{ch:concrete-instances-fourier-namecert} and the finite Parseval energy-identity surface of \autoref{ch:concrete-instances-parseval-namecert}. The route may expose Fourier coefficient windows, Parseval finite-energy ledgers, circle samples, inner-product pairings, integral observations, rational readback, dyadic tolerances, and Real seals, but it exports no ambient Plancherel theorem, inversion theorem, completed Hilbert-space norm equality, host function equality, selected representative, or quotient coefficient class.
\end{theorem}
\begin{proof}
Start with the rows $F$ and $V$ of \autoref{def:finite-fourier-energy-carrier}. The row $F$ is explicitly the finite Fourier observation row, while $V$ is explicitly the finite Parseval identity row.

Attach the source, pairing, and energy rows $S,I,J$. They keep the route on finite circle samples, inner-product witnesses, and integral observations rather than on a completed ambient transform.

Read $Q,D,R$ next. Rational readback and dyadic tolerance data are visible before the Real seal, so the terminal row is only the displayed finite energy comparison.

The non-energy rows $H,C,P,N$ preserve this same factorization under transport, replay, provenance, and naming. Therefore every consumer route factors through the Fourier and Parseval siblings and stops before the excluded Plancherel, inversion, completion, host-equality, representative-selection, or quotient conclusions.
\end{proof}

\falsifiablePrediction{Every $\FiniteFourierEnergyUp$ energy read factors through Fourier finite observations, Parseval finite-energy ledgers, circle source samples, InnerProduct pairings, Integral energy observations, RegSeqRat rational readback, DyadicRatCore tolerances, Real seals, hsame transport, Cont replay, Pkg provenance, and local naming.}

\independenceWitness{fourier, parseval, s1, innerproduct, integral, regseqrat, dyadicratcore, real: $\FiniteFourierEnergyUp$ is not bijective to any listed sibling because it jointly carries the finite Fourier observation row, finite Parseval identity row, source, pairing, integral, rational-readback, dyadic-tolerance, Real-seal, transport, replay, provenance, and local naming rows.}

\closureat{FiniteFourierEnergyUp}{seedStr}

\begin{closurestatus}{\FiniteFourierEnergyUp}
  \constructivestory{A $\FiniteFourierEnergyUp$ packet is generated from finite Fourier observations, a finite Parseval identity row, circle source samples, inner-product pairings, integral energy observations, rational readback, dyadic tolerance accounting, a terminal Real seal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:finite-fourier-energy-carrier}, \autoref{thm:finite-fourier-energy-namecert-obligations}, and \autoref{thm:finite-fourier-energy-parseval-route} seed the finite Fourier energy certificate consumed by downstream Plancherel-facing work.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient Plancherel, Fourier inversion, convergence closure, completed Hilbert-space norm equality, host function equality, selected representatives, quotient coefficient classes, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, Fourier-window exactness, Parseval-row attachment, circle-source exposure, inner-product and integral-energy accounting, rational readback, dyadic tolerance accounting, Real seal non-escape, transport, replay, provenance, local naming, and TasteGate field faithfulness for BEDC.Derived.FiniteFourierEnergyUp.}
\end{closurestatus}
