\chapter{A Concrete Naming Certificate for $\CatZeroMetricUp$}
\label{ch:concrete-instances-cat-zero-metric-namecert}
\origin{human}

Following the Cartan--Alexandrov--Toponogov comparison tradition and the metric treatment of Bridson--Haefliger, the $\CatZeroMetricUp$ packet records a finite nonpositive-curvature comparison surface inside BEDC. It sits over the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, the finite segment witness of \autoref{ch:concrete-instances-geodesic-metric-namecert}, the convex subset rows of \autoref{ch:concrete-instances-convexset-namecert}, and the completion handoff of \autoref{ch:concrete-instances-completemetric-namecert}. The packet names comparison-triangle data for displayed geodesic windows; it is not a host path space, not a selected geodesic object, not a quotient path-equality principle, and not an ambient Hadamard-space theorem.

\begin{definition}[CAT(0) metric carrier]
\label{def:cat-zero-metric-carrier}
A $\CatZeroMetricUp$ carrier is a finite $\BHist$ packet
$$
Z=(M,G,V,E,A,Q,D,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the source $\MetricUp$ row, carrying only the displayed point classifier, distance rows, and metric-law ledger.
\item $G$ is the $\GeodesicMetricUp$ row that names the finite segment windows used by the comparison request.
\item $V$ is the finite vertex triple row $(x,y,z)$, with each vertex admitted through the point classifier of $M$.
\item $E$ is the edge-segment row, displaying the three geodesic windows between $x,y,z$ through $G$.
\item $A$ is the Alexandrov comparison-triangle row. It records the Euclidean side-length readback and the comparison point parameters for the displayed edge windows.
\item $Q$ is the CAT(0) comparison ledger. For each displayed pair of comparison parameters on the triangle edges, it stores the finite inequality saying that the metric distance in $M$ is bounded by the corresponding Euclidean comparison distance.
\item $D$ is the $\ConvexSetUp$ domain row for each displayed convex window on which the comparison read is consumed.
\item $L$ is the $\CompleteMetricUp$ handoff row. It exposes the completion-facing read of the same finite comparison window without asserting that the ambient space is complete.
\item $H$ records componentwise $\hsame$ transport for the metric row, geodesic row, vertex triple, edge windows, comparison-triangle row, inequality ledger, convex window, completion handoff, continuation replay, provenance, and local naming.
\item $C$ records displayed $\Cont$ replay from a finite comparison request through
$$
M,G,V,E,A,Q,D,L \longmapsto H,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\CatZeroMetricUp$, $\MetricUp$, $\GeodesicMetricUp$, $\ConvexSetUp$, $\CompleteMetricUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\CatZeroMetricUp}$ row.
\end{enumerate}
The carrier has no coordinate for a global CAT(0) existence theorem, selected geodesics, host Euclidean realization, quotient path equality, full convex projection operator, or ambient completeness.
\end{definition}

\begin{theorem}[CAT(0) metric comparison obligations]
\label{thm:cat-zero-metric-comparison-obligations}
For every accepted $\CatZeroMetricUp$ carrier
$$
Z=(M,G,V,E,A,Q,D,L,H,C,P,N),
$$
the local $\NameCert_{\CatZeroMetricUp}$ surface consists exactly of metric-source admission, geodesic segment-window admission, displayed vertex-triple admission, comparison-triangle readback, CAT(0) inequality ledger exactness, convex-window handoff, complete-metric handoff, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local naming over the rows of \autoref{def:cat-zero-metric-carrier}.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:cat-zero-metric-carrier}. The accepted packet displays exactly the metric source, geodesic row, vertex triple, edge windows, comparison-triangle row, inequality ledger, convex handoff, completion handoff, transport, replay, provenance, and naming coordinates.

The comparison obligation is the role of $A$ and $Q$. Row $A$ gives the Euclidean side-length and parameter readback for the displayed triangle, while $Q$ records only the finite distance inequalities requested by the CAT(0) comparison.

Rows $D$ and $L$ keep downstream consumers attached to the displayed convex and complete-metric surfaces. The structural rows $H,C,P,N$ transport, replay, source, and name the same finite data, so no obligation row can be read as a selected geodesic, host Euclidean construction, quotient path equality, or ambient completeness theorem.
\end{proof}

\begin{theorem}[CAT(0) metric projection non-escape]
\label{thm:cat-zero-metric-projection-nonescape}
Every convex-projection or completion-facing consumer of an accepted $\CatZeroMetricUp$ packet must factor through the finite route
$$
\MetricUp,\ \GeodesicMetricUp,\ \ConvexSetUp,\ \CompleteMetricUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
It may consume displayed comparison-triangle inequalities for the named convex window, but it cannot infer a global nearest-point projection map, a general Hadamard-space theorem, selected geodesics, quotient path equality, or ambient completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:cat-zero-metric-comparison-obligations}. It exposes a convex-projection-facing or completion-facing read only after the metric source, geodesic windows, vertex triple, comparison-triangle row, and CAT(0) inequality ledger have all been displayed.

The displayed continuation route then passes through $D$ and $L$. Thus a convex consumer reads the comparison ledger as finite certificate data for the shown window, and a completion consumer reads the same window through the complete-metric handoff rather than through a global completeness assertion.

Inspecting the carrier definition gives the exclusion. There is no coordinate for a full projection operator, selected geodesic family, host Hadamard-space theorem, quotient path equality, or ambient completeness, so any consumer requiring one of those objects is outside the local classifier.
\end{proof}

\closureat{CatZeroMetricUp}{seedStr}

\begin{closurestatus}{\CatZeroMetricUp}
  \constructivestory{A $\CatZeroMetricUp$ packet is generated from a MetricUp source, a GeodesicMetricUp segment-window row, a displayed vertex triple, comparison edge rows, an Alexandrov comparison-triangle readback, a finite CAT(0) inequality ledger, ConvexSetUp and CompleteMetricUp handoff rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:cat-zero-metric-carrier}, \autoref{thm:cat-zero-metric-comparison-obligations}, and \autoref{thm:cat-zero-metric-projection-nonescape} seed the finite CAT(0) comparison route from displayed metric and geodesic data through convex and complete-metric consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a global Hadamard-space theorem, selected geodesics, quotient path equality, a full nearest-point projection operator, ambient completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, comparison-triangle readback exactness, CAT(0) inequality-ledger stability, convex-window handoff, completion handoff, and BEDC.Derived.CatZeroMetricUp formalization.}
\end{closurestatus}
