\chapter{A Concrete Naming Certificate for $\TriebelLizorkinSpaceUp$}
\label{ch:concrete-instances-triebel-lizorkin-space-namecert}
\origin{human}

Following Triebel--Lizorkin theory and constructive regularity spaces, the $\TriebelLizorkinSpaceUp$ packet records the finite mixed scale-position surface by which a smoothness request can inspect local dyadic data before aggregating it into a global regularity name. It sits beside the Besov aggregate of \autoref{ch:concrete-instances-besov-space-namecert}, the Sobolev weak-gradient ledger of \autoref{ch:concrete-instances-sobolev-namecert}, the Holder pointwise boundary of \autoref{ch:concrete-instances-holder-continuity-namecert}, the weak-derivative action row of \autoref{ch:concrete-instances-weak-derivative-namecert}, the dyadic scale budget of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet names only finite scale windows, local position probes, mixed aggregation rows, dyadic tolerances, regular rational readback, real seals, transport, replay, provenance, and local naming; it does not assert a completed distribution space, Littlewood--Paley decomposition equality, quotient function identity, countable choice, or ambient $\RealUp$ completeness.

\begin{definition}[Triebel--Lizorkin space carrier]
\label{def:triebel-lizorkin-space-carrier}
A $\TriebelLizorkinSpaceUp$ carrier is a finite $\BHist$ packet
$$
T=(S,Hd,W,D,R,E,Q,L,A,M,G,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the $\SobolevUp$ source row, recording the weak-gradient and integrability ledger consumed by the local regularity request.
\item $Hd$ is the $\HolderContinuityUp$ boundary row, recording the visible power-law control used when the packet exposes pointwise smoothness data.
\item $W$ is the $\WeakDerivativeUp$ action row, naming the finite test probes and derivative observations inspected by the scale-position request.
\item $D$ is the $\DyadicRatCoreUp$ scale ledger, recording dyadic scale, radius, and comparison budgets for each displayed window.
\item $R$ is the $\RegSeqRatUp$ readback row for the regular rational magnitudes attached to the selected scale-position cells.
\item $E$ is the terminal $\RealUp$ seal row reached only after $S,Hd,W,D,R$ have been displayed.
\item $Q$ is the finite window schedule selecting the visible scale levels, local position probes, and comparison requests carried by this packet.
\item $L$ is the local position-bundle row, recording the finite family of probe locations attached to each visible dyadic scale.
\item $A$ is the mixed aggregation row. It records that local position data is aggregated inside each scale before the global regularity request is named.
\item $M$ is the Besov comparison row, exposing the difference between the Triebel--Lizorkin mixed scale-position route and the aggregate Besov route of \autoref{ch:concrete-instances-besov-space-namecert}.
\item $G$ stores componentwise $\hsame$ transport for the source, boundary, weak-action, dyadic, regular-rational, real-seal, window, local-position, mixed-aggregation, Besov-comparison, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from a Triebel--Lizorkin regularity request through
$$
S,Hd,W,D,R,E,Q,L,A,M \longmapsto G,P,N .
$$
\item $P$ is the $\Pkg$ provenance over $\TriebelLizorkinSpaceUp$, $\BesovSpaceUp$, $\SobolevUp$, $\HolderContinuityUp$, $\WeakDerivativeUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\TriebelLizorkinSpaceUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only through $S,Hd,W,D,R,E,Q,L,A,M,G,C,P,N$. It has no coordinate for a completed distribution space, quotient equality of function spaces, selected Littlewood--Paley representatives, host equality of local probes, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Triebel--Lizorkin space NameCert obligations]
\label{thm:triebel-lizorkin-space-namecert-obligations}
For every accepted $\TriebelLizorkinSpaceUp$ carrier
$$
T=(S,Hd,W,D,R,E,Q,L,A,M,G,C,P,N),
$$
the local $\NameCert_{\TriebelLizorkinSpaceUp}$ surface consists exactly of carrier admission for the displayed Sobolev row, Holder row, weak-derivative action row, dyadic scale ledger, regular rational readback row, terminal real seal, finite window schedule, local position bundle, mixed aggregation row, Besov comparison row, componentwise transport, displayed replay, provenance, and local naming rows. Every PDE, trace, interpolation, or nonlinear regularity consumer of the packet must read through those rows before it cites the Triebel--Lizorkin smoothness boundary.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:triebel-lizorkin-space-carrier}. The source rows are $S,Hd,W$, the scale and readback rows are $D,R,E,Q$, the mixed scale-position rows are $L,A,M$, and the structural rows are $G,C,P,N$.

The Sobolev, Holder, and weak-derivative rows supply the analytic source surface. The Sobolev row carries weak-gradient and integrability data, the Holder row carries the visible pointwise boundary, and the weak-derivative row carries the finite test-action observations.

The dyadic, regular-rational, and real-seal rows fix the numerical part of the packet. The window schedule $Q$ selects the displayed scale levels, $D$ attaches the tolerance budget, $R$ reads back the regular rational magnitudes, and $E$ seals the resulting real-facing data.

The local position bundle $L$ and mixed aggregation row $A$ are the Triebel--Lizorkin-specific surface. The Besov comparison row $M$ records that the packet keeps scale and position coupled before a global regularity name is exported.

Finally $G,C,P,N$ transport, replay, source, and name the same finite route. Since no completed distribution space, quotient function-space equality, selected Littlewood--Paley representative, host equality of probes, countable choice, or ambient completeness coordinate appears in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Triebel--Lizorkin dyadic scale route]
\label{thm:triebel-lizorkin-space-dyadic-scale-route}
Every L10 or L11 regularity consumer of an accepted $\TriebelLizorkinSpaceUp$ carrier factors through the finite route
$$
\SobolevUp,\quad \WeakDerivativeUp,\quad \HolderContinuityUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,\quad \BesovSpaceUp,\quad \BHist,\quad \hsame,\quad \Cont,\quad \Pkg,\quad \NameCert .
$$
The route exports local scale-position windows, dyadic tolerance control, regular rational readback, terminal real seals, the explicit comparison with the Besov aggregate, componentwise transport, continuation replay, provenance, and local naming. It exports no completed distribution space, quotient function space, selected Littlewood--Paley representative, host equality of functions or local probes, countable-choice row, or ambient $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations of \autoref{thm:triebel-lizorkin-space-namecert-obligations}. They require every accepted regularity read to pass through the Sobolev, Holder, and weak-derivative rows before any downstream smoothness boundary is cited.

Next read the finite scale-position data. The window schedule $Q$ chooses the visible dyadic levels, the local position bundle $L$ records the probe locations at those levels, and the mixed aggregation row $A$ keeps those observations coupled before the global name is exported.

The dyadic ledger $D$, regular rational row $R$, and terminal real seal $E$ report the numerical data attached to the same windows. The Besov comparison row $M$ exposes the sibling aggregate route without identifying the two carriers.

Thus an L10 or L11 consumer receives exactly the displayed chain from Sobolev and weak-derivative evidence through Holder, dyadic, regular-rational, real-seal, Besov-comparison, and structural rows. The excluded distribution-space, quotient, representative-selection, host-equality, choice, and ambient-completeness objects have no carrier coordinate and cannot be exported by the packet.
\end{proof}

\falsifiablePrediction{Every accepted $\TriebelLizorkinSpaceUp$ regularity consumer must read Sobolev, HolderContinuity, WeakDerivative, DyadicRatCore, RegSeqRat, Real, BesovSpace, local position-bundle, mixed aggregation, hsame, Cont, Pkg, and local NameCert rows before citing the Triebel--Lizorkin smoothness boundary.}

\independenceWitness{besov-space, sobolev, holder-continuity, weak-derivative, dyadicratcore, regseqrat, real: $\TriebelLizorkinSpaceUp$ is not bijective to any listed sibling because it jointly carries smoothness-source rows, local scale-position probes, mixed aggregation, dyadic scale budgets, regular rational readback, real seals, Besov comparison, transport, replay, provenance, and local naming.}

\closureat{TriebelLizorkinSpaceUp}{seedStr}

\begin{closurestatus}{\TriebelLizorkinSpaceUp}
  \constructivestory{A $\TriebelLizorkinSpaceUp$ packet is generated from Sobolev, HolderContinuity, WeakDerivative, DyadicRatCore, RegSeqRat, Real, finite window, local position-bundle, mixed aggregation, Besov comparison, componentwise hsame, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:triebel-lizorkin-space-carrier}, \autoref{thm:triebel-lizorkin-space-namecert-obligations}, and \autoref{thm:triebel-lizorkin-space-dyadic-scale-route} seed the finite constructive Triebel--Lizorkin route over Sobolev, HolderContinuity, WeakDerivative, DyadicRatCore, RegSeqRat, Real, BesovSpace, BHist, hsame, Cont, Pkg, and NameCert rows.}
  \formalstatus{\unformalizedV}
  \leanstmt{BEDC.Derived.TriebelLizorkinSpaceUp}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim Lean verification, completed distribution spaces, Littlewood--Paley representative selection, quotient function spaces, host equality of functions or probes, countable choice, ambient Real completeness, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, local scale-position window exactness, mixed aggregation stability, dyadic-scale ledger stability, regular rational readback, Real seal nonescape, Besov comparison, transport, replay, provenance, and local naming for BEDC.Derived.TriebelLizorkinSpaceUp.}
\end{closurestatus}
