\chapter{A Concrete Naming Certificate for $\KaramataInequalityUp$}
\label{ch:concrete-instances-karamata-inequality-namecert}
\origin{human}

Following Hardy--Littlewood--Polya, the $\KaramataInequalityUp$ packet records the finite majorization route by which a convex-function row and two ordered finite vector rows produce the Karamata comparison. It consumes the Jensen route of \autoref{ch:concrete-instances-jensen-inequality-namecert}, the convex-carrier surface of \autoref{ch:concrete-instances-convexset-namecert}, the rational coefficient source of \autoref{ch:concrete-instances-rat-namecert}, the vector carrier of \autoref{ch:concrete-instances-vecspace-namecert}, the real-name boundary of \autoref{ch:concrete-instances-real-namecert}, and the endpoint comparison discipline of \autoref{ch:concrete-instances-real-min-max-namecert}. The packet names the traditional majorization inequality as finite BEDC data; it does not import a host convex function, quotient equality of real names, selected extrema, trichotomy, countable choice, or ambient real completeness.

\begin{definition}[Karamata inequality carrier]
\label{def:karamata-inequality-carrier}
A $\KaramataInequalityUp$ carrier is a finite $\BHist$ packet
$$
K=(F,X,Y,M,A,J,R,Q,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the convex-function source row, including the displayed domain, codomain, convexity ledger, and function-read route.
\item $X$ and $Y$ are the two finite vector rows over $\VecSpaceUp$, with their coordinate reads and finite ordering windows.
\item $M$ is the majorization ledger, recording the prefix-sum comparisons, total-sum agreement, and rational coefficient witnesses read through $\RatUp$ and $\RealUp$.
\item $A$ is the $\ConvexSetUp$ affine-spine row certifying that the Jensen decompositions used by the comparison stay inside the displayed convex carrier.
\item $J$ is the $\JensenInequalityUp$ handoff row, recording the finite Jensen calls used to convert the majorization ledger into image-sum comparisons.
\item $R$ is the $\RealUp$ comparison row for the displayed sum of convex images.
\item $Q$ is the $\RealMinMaxUp$ endpoint row used when a consumer reads the ordered finite comparison.
\item $H$ records componentwise $\hsame$ transport for $F,X,Y,M,A,J,R,Q$ and the local naming row.
\item $C$ records displayed $\Cont$ replay from majorization rows through the Jensen handoff, real comparison, endpoint row, provenance, and local name.
\item $P$ is the $\Pkg$ provenance over $\KaramataInequalityUp$, $\JensenInequalityUp$, $\ConvexSetUp$, $\RatUp$, $\VecSpaceUp$, $\RealUp$, $\RealMinMaxUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\KaramataInequalityUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $F,X,Y,M,A,J,R,Q,H,C,P,N$. It has no coordinate for a host convex function, quotient equality of real names or functions, selected rearrangements, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Karamata inequality NameCert obligations]
\label{thm:karamata-inequality-namecert-obligations}
For every accepted $\KaramataInequalityUp$ carrier $K=(F,X,Y,M,A,J,R,Q,H,C,P,N)$, the local $\NameCert_{\KaramataInequalityUp}$ surface consists exactly of carrier admission for the convex-function source row, the two finite vector rows, the majorization ledger, the convex-set affine-spine row, the Jensen handoff row, the real comparison row, the endpoint row, structural rows $H,C,P$, and local naming row $N$; prefix-sum and total-sum accountability through $M$; affine-spine accountability through $A$; Jensen-mediated comparison through $J,R,Q$; and componentwise transport, replay, provenance, and naming for the same finite route.
\end{theorem}
\begin{proof}
Project the accepted packet $K=(F,X,Y,M,A,J,R,Q,H,C,P,N)$. The carrier definition exposes exactly the convex-function source, finite vector inputs, majorization ledger, affine-spine route, Jensen handoff, real comparison, endpoint comparison, transport, replay, provenance, and naming rows.

The majorization ledger $M$ is read before the inequality row. It supplies the prefix-sum comparisons, total-sum agreement, and rational coefficient witnesses, while $A$ supplies the displayed $\ConvexSetUp$ route that keeps each Jensen decomposition inside the accepted convex carrier.

The handoff row $J$ then invokes only the already displayed Jensen certificate. The comparison rows $R,Q$ carry the resulting real and endpoint comparisons, and $H,C,P,N$ preserve and name that route. Since no host convex-function object, quotient equality, selected rearrangement, or ambient completeness coordinate is present, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Karamata inequality Jensen-majorization handoff]
\label{thm:karamata-inequality-jensen-majorization-handoff}
Every accepted $\KaramataInequalityUp$ packet routes its public comparison through
$$
X,Y,M \longmapsto A \longmapsto J \longmapsto R,Q \longmapsto H,C,P,N .
$$
Consequently a consumer must read the two finite vector rows, the majorization ledger, the $\ConvexSetUp$ affine-spine row, the $\JensenInequalityUp$ handoff row, the $\RealUp$ comparison row, the $\RealMinMaxUp$ endpoint row, componentwise transport, replay, provenance, and local naming before it can cite the Karamata inequality surface.
\end{theorem}
\begin{proof}
Start with a consumer read of the Karamata comparison. By \autoref{def:karamata-inequality-carrier}, the only majorization data are the vector rows $X,Y$ and the ledger $M$.

The affine-spine row $A$ is downstream of those finite rows. It keeps the displayed decompositions inside the same convex carrier before any Jensen call is read.

Apply the Jensen handoff row $J$. It is a reference to the finite NameCert surface of \autoref{ch:concrete-instances-jensen-inequality-namecert}, so the consumer receives the Jensen comparison only after the majorization and affine-spine data have been displayed.

Finally $R,Q,H,C,P,N$ expose the real comparison, endpoint comparison, transport, replay, provenance, and local naming. Thus no consumer can bypass the finite majorization route by invoking a host convexity theorem or ambient real-completeness principle.
\end{proof}

\falsifiablePrediction{Every $\KaramataInequalityUp$ consumer reads a convex-function source row, two finite VecSpace rows, a majorization ledger, a ConvexSet affine-spine row, a JensenInequality handoff row, Real comparison rows, RealMinMax endpoint rows, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local naming before the Karamata inequality surface is public.}

\independenceWitness{jenseninequality, convexset, rat, vecspace, real, realminmax: $\KaramataInequalityUp$ is not bijective to any listed sibling because it jointly carries two ordered finite vector rows, a majorization ledger, affine-spine data, Jensen handoff, real comparison, endpoint comparison, transport, replay, provenance, and local NameCert data as one finite inequality packet.}

\closureat{KaramataInequalityUp}{seedStr}

\begin{closurestatus}{\KaramataInequalityUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:karamata-inequality-carrier}, \autoref{thm:karamata-inequality-namecert-obligations}, and \autoref{thm:karamata-inequality-jensen-majorization-handoff} seed the finite Karamata inequality route over convex-function, majorization, Jensen, ConvexSet, Rat, VecSpace, Real, and RealMinMax rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close host convex functions, quotient equality of real names or functions, selected rearrangements, trichotomy, countable choice, ambient $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, majorization ledger accountability, ConvexSet affine-spine exactness, Jensen handoff exactness, Real comparison nonescape, endpoint comparison handoff, and public export scope for BEDC.Derived.KaramataInequalityUp.}
  \constructivestory{A $\KaramataInequalityUp$ packet is generated from a convex-function source row, two finite VecSpace rows, a majorization ledger, a ConvexSet affine-spine row, a JensenInequality handoff row, Real comparison rows, RealMinMax endpoint rows, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
\end{closurestatus}
