\chapter{Rising Sun Lemma NameCert Construction}
\label{ch:concrete-instances-rising-sun-lemma-namecert}
\origin{human}

Following Riesz's rising sun lemma, the $\RisingSunLemmaUp$ packet records the finite BEDC surface for decomposing a located real interval into exposed and shaded subinterval windows for an upper-envelope comparison. It is a neighbour of the real-name boundary of \autoref{ch:concrete-instances-real-namecert}, the located-real route of \autoref{ch:concrete-instances-locatedreal-namecert}, the dyadic interval rows of \autoref{ch:concrete-instances-dyadicinterval-namecert}, and the compact interval maximum route of \autoref{ch:concrete-instances-compact-interval-maximum-namecert}. The chapter isolates only the finite interval-decomposition certificate consumed by later $\RealUp$ analysis; it does not import a host measurable decomposition, selected family of open intervals, countable choice, or ambient completeness of $\RealUp$.

\begin{definition}[RisingSunLemma carrier]
\label{def:rising-sun-carrier}
A $\RisingSunLemmaUp$ carrier is a finite $\BHist$ packet
$$
\mathsf{RisingSunLemma}(I,F,E,M,S,T,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $I$ is the compact located interval row, read through the displayed $\RealUp$ endpoint names and the dyadic-interval subdivision ledger;
\item $F$ is the located upper-envelope observation row on the interval;
\item $E$ is the exposed-window ledger, listing finite dyadic subintervals on which the observation sits below a later envelope read;
\item $M$ is the compact interval maximum handoff row used to certify the local envelope bound on each displayed closed window;
\item $S$ is the shaded-window complement ledger, recording the remaining finite interval pieces after the exposed windows are read;
\item $T$ is the terminal $\RealUp$ handoff row through which downstream consumers read the endpoint and envelope seals;
\item $H$ is the componentwise $\hsame$ transport over the interval, observation, maximum, exposed-window, shaded-window, and terminal rows;
\item $C$ is the displayed $\Cont$ replay route for the same rows;
\item $P$ is the $\Pkg$ provenance over $\RisingSunLemmaUp$, $\RealUp$, $\LocatedRealUp$, $\DyadicIntervalUp$, $\CompactIntervalMaximumUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RisingSunLemmaUp}$ row.
\end{enumerate}
\end{definition}

\begin{theorem}[RisingSunLemma NameCert obligations]
\label{thm:rising-sun-namecert-obligations}
For every accepted $\RisingSunLemmaUp$ carrier
$$
R=\mathsf{RisingSunLemma}(I,F,E,M,S,T,H,C,P,N),
$$
the local $\NameCert_{\RisingSunLemmaUp}$ surface consists exactly of compact located interval admission through $I$, located upper-envelope readback through $F$, exposed-window visibility through $E$, compact interval maximum handoff through $M$, shaded-window complement visibility through $S$, terminal $\RealUp$ seal readback through $T$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.

The obligation rows are finite. The $\BHist$ row stores only displayed dyadic subinterval packets and real-name observations; the $\hsame$ row transports the interval, envelope, maximum, exposed-window, shaded-window, and terminal rows componentwise; the $\Cont$ row replays the same finite inspection route; the $\Pkg$ row records provenance through the Real, located-real, dyadic-interval, and compact-maximum siblings; and the $\NameCert$ row admits no extra decomposition datum outside these rows.
\end{theorem}
\begin{proof}
Start from the carrier rows in \autoref{def:rising-sun-carrier}. The interval and endpoint data are already displayed as $\RealUp$ and located-real rows, while the subdivision data are finite dyadic interval rows.

Apply the compact interval maximum handoff to each displayed closed window in the finite dyadic ledger. This binds the envelope comparison to $M$ before the exposed and shaded ledgers are consumed by any downstream real-analysis route.

The remaining structural rows are bookkeeping over the same finite packet. Componentwise $\hsame$ transport preserves each displayed interval and envelope row, $\Cont$ replay keeps the finite inspection order, $\Pkg$ records the sibling provenance, and $N$ names the resulting local surface. Since the carrier contains no selected open family, no quotient real equality, no countable-choice row, and no ambient completeness coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[RisingSunLemma stopping-time handoff]
\label{thm:rising-sun-stopping-time-handoff}
Every downstream stopping-time or finite-sweep consumer of an accepted $\RisingSunLemmaUp$ carrier factors through the exposed-window ledger $E$, the compact interval maximum handoff $M$, the shaded-window complement ledger $S$, and the terminal $\RealUp$ row $T$ before it can read an interval-decomposition result. The handoff is therefore a finite interval decomposition over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, not a selected countable union of open intervals, not quotient equality of real endpoints, and not an appeal to ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the accepted carrier in the order displayed by the packet. A stopping-time consumer first sees the compact located interval row and the finite dyadic subdivision ledger, so every candidate exposed window is already a finite interval row.

The envelope comparison is then routed through the compact interval maximum handoff. This supplies the local maximum row used to certify whether a window is exposed or remains in the shaded complement, without selecting an external family of intervals.

Finally the downstream consumer reads the terminal $\RealUp$ handoff through the displayed transport, replay, provenance, and naming rows. Thus every stopping-time read is a finite handoff through $E,M,S,T,H,C,P,N$, and no unlisted choice, quotient, bridge, or completeness datum can supply an alternate decomposition.
\end{proof}
