\chapter{A Concrete Naming Certificate for $\DunfordPettisUp$}
\label{ch:concrete-instances-dunford-pettis-namecert}
\origin{human}

Following Dunford and Pettis on weak compactness in $L^{1}$ spaces, the $\DunfordPettisUp$ packet records the finite BEDC surface on which weak compactness is handed to uniform integrability before any selected weakly compact subsequence, countable-choice schedule, quotient almost-everywhere equality, or ambient Banach-space compactness theorem is public. It sits beside the measure and integral sources of \autoref{ch:concrete-instances-measure-namecert} and \autoref{ch:concrete-instances-integral-namecert}, the tail-budget packet of \autoref{ch:concrete-instances-uniform-integrability-namecert}, the functional-analysis carrier of \autoref{ch:concrete-instances-functionalanalysis-namecert}, and the bounded-operator surface of \autoref{ch:concrete-instances-boundedlinearoperator-namecert}.

\begin{definition}[Dunford-Pettis carrier]
\label{def:dunford-pettis-carrier}
A $\DunfordPettisUp$ carrier is a finite $\BHist$ packet
$$
D=(U,M,I,F,B,R,W,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $U$ is the $\UniformIntegrabilityUp$ source row naming the family-level tail budget.
\item $M$ is the $\MeasureUp$ source row through which measurable domains, measurable sets, and finite-measure windows are read.
\item $I$ is the $\IntegralUp$ readback row for displayed $L^{1}$ bounds and tail integrals.
\item $F$ is the $\FunctionalAnalysisUp$ row naming the weak topology, dual-pairing probes, and finite neighborhood tests visible to the packet.
\item $B$ is the $\BoundedLinearOperatorUp$ row for bounded linear probes used to inspect weak images.
\item $R$ is the $\RealUp$ budget row storing scalar tolerances, norm bounds, and finite comparison windows.
\item $W$ is the weak-compactness handoff row. It records only the finite implication route from uniform-integrability evidence through weak-probe tests to the consumer-visible compactness request.
\item $H$ records componentwise $\hsame$ transport for $U,M,I,F,B,R,W$ and the local structural rows.
\item $C$ records displayed $\Cont$ replay from weak-compactness requests through $U,M,I,F,B,R,W,H,P,N$.
\item $P$ is the $\Pkg$ provenance over $\DunfordPettisUp$, $\UniformIntegrabilityUp$, $\MeasureUp$, $\IntegralUp$, $\FunctionalAnalysisUp$, $\BoundedLinearOperatorUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\DunfordPettisUp}$ row.
\end{enumerate}
The carrier has no coordinate for a selected weakly compact subsequence, countable choice, quotient almost-everywhere equality, ambient Banach-space compactness, a host dual-ball compactness theorem, or an unbounded family of weak probes.
\end{definition}

\begin{theorem}[Dunford-Pettis NameCert obligations]
\label{thm:dunford-pettis-namecert-obligations}
For every accepted $\DunfordPettisUp$ carrier
$$
D=(U,M,I,F,B,R,W,H,C,P,N),
$$
the local $\NameCert_{\DunfordPettisUp}$ surface consists exactly of carrier admission for the displayed rows, uniform-integrability source compatibility through $U$, measure source compatibility through $M$, integral readback through $I$, weak-test visibility through $F$, bounded-probe visibility through $B$, scalar-budget visibility through $R$, weak-compactness handoff through $W$, componentwise transport through $H$, displayed replay through $C$, package provenance through $P$, and local naming through $N$.

Every weak-compactness-facing consumer must read the same rows before using the handoff. It receives no selected subsequence, no countable-choice schedule, no quotient almost-everywhere equality, no ambient Banach-space compactness theorem, no host dual-ball compactness theorem, and no infinite probe family.
\end{theorem}
\begin{proof}
Carrier admission is projection from \autoref{def:dunford-pettis-carrier}. The accepted packet displays exactly $U,M,I,F,B,R,W,H,C,P,N$.

The analytic source rows $U,M,I$ fix the uniform-integrability, measure, and integral surfaces. The weak-facing rows $F$ and $B$ then limit the consumer to the displayed weak topology tests and bounded linear probes, while $R$ supplies only the scalar budgets visible in the packet.

The handoff row $W$ is downstream of those rows. It records the finite implication route from uniform integrability to weak compactness, but it does not choose a subsequence, quotient representatives, or a host compactness theorem.

The structural rows $H,C,P,N$ preserve that same packet under transport, replay, provenance, and naming. Since every excluded object has no carrier coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Dunford-Pettis uniform-integrability handoff]
\label{thm:dunford-pettis-uniform-integrability-handoff}
Every weak-compactness consumer of an accepted $\DunfordPettisUp$ carrier reaches the Dunford-Pettis handoff only through the displayed route
$$
U \longmapsto M,I \longmapsto F,B,R \longmapsto W \longmapsto H,C,P,N .
$$
Thus the consumer may read the uniform-integrability budget, measure and integral evidence, finite weak-test and bounded-probe rows, scalar bounds, the weak-compactness handoff, transport, replay, provenance, and local naming, and it may not read selected weakly compact subsequences, countable choice, quotient almost-everywhere equality, ambient Banach-space compactness, host dual-ball compactness, or unbounded weak-probe families.
\end{theorem}
\begin{proof}
Begin with a weak-compactness-facing read. By \autoref{def:dunford-pettis-carrier}, the only tail-control source is $U$, and it is interpreted only through the displayed measure and integral rows $M$ and $I$.

The weak tests then pass through $F$ and $B$. These rows expose finite dual-pairing and bounded-operator probes, while $R$ records the scalar comparison budgets needed by those probes.

The consumer reaches weak compactness only at $W$. That row is a handoff from the already displayed uniform-integrability data to the public weak-compactness request, not an extraction of a subsequence or a compactness theorem from an ambient Banach space.

Finally $H,C,P,N$ transport, replay, package, and name the same route. Because the carrier lacks coordinates for the refused objects, no consumer can recover them from the Dunford-Pettis packet.
\end{proof}

\falsifiablePrediction{Any $\DunfordPettisUp$ read that claims weak compactness while bypassing the displayed $\UniformIntegrabilityUp$, $\MeasureUp$, $\IntegralUp$, $\FunctionalAnalysisUp$, $\BoundedLinearOperatorUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows refutes the carrier of \autoref{def:dunford-pettis-carrier}.}

\independenceWitness{uniform-integrability, measure, integral, functional-analysis, bounded-linear-operator: $\DunfordPettisUp$ is not bijective to any listed sibling because it stores the finite weak-compactness handoff row over the shared tail-control and weak-probe sources without storing selected subsequences, countable choice, quotient almost-everywhere equality, or ambient compactness.}

\closureat{DunfordPettisUp}{seedStr}

\begin{closurestatus}{\DunfordPettisUp}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:dunford-pettis-carrier}, \autoref{thm:dunford-pettis-namecert-obligations}, and \autoref{thm:dunford-pettis-uniform-integrability-handoff} seed the finite handoff from uniform integrability to weak compactness over measure, integral, weak-test, bounded-probe, scalar-budget, transport, replay, provenance, and local naming rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim selected weakly compact subsequences, countable choice, quotient almost-everywhere equality, ambient Banach-space compactness, host dual-ball compactness, unbounded weak-probe families, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, uniform-integrability source compatibility, measure and integral readback, weak-test visibility, bounded-probe visibility, scalar-budget visibility, handoff nonescape, transport, replay, provenance, and local naming for BEDC.Derived.DunfordPettisUp.}
  \constructivestory{A $\DunfordPettisUp$ packet is generated from UniformIntegrability, Measure, Integral, FunctionalAnalysis, BoundedLinearOperator, Real scalar-budget, weak-compactness handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
\end{closurestatus}
