\chapter{A Concrete Naming Certificate for $\UniformCauchyCompletionRealizerUp$}
\label{ch:concrete-instances-uniform-cauchy-completion-realizer-namecert}
\origin{human}

Following Bishop and Bridges on constructive Cauchy completion, the $\UniformCauchyCompletionRealizerUp$ packet records the finite realizer surface that turns a uniform completion datum into a real-name seal. It sits after the functorial completion route of \autoref{ch:concrete-instances-uniformcompletionfunctor-namecert}, the dyadic tolerance core of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream-window surface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readback route of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal real-name seal of \autoref{ch:concrete-instances-real-namecert}. The packet supplies a displayed modulus-governed realizer for L10 completion reads without importing quotient completions, selected limits, host complete spaces, choice, or ambient completeness of $\RealUp$.

\begin{definition}[UniformCauchyCompletionRealizer carrier]
\label{def:uniform-cauchy-completion-realizer-carrier}
A $\UniformCauchyCompletionRealizerUp$ carrier is a finite $\BHist$ packet
$$
U=(F,D,W,R,M,E,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $F$ is the $\UniformCompletionFunctorUp$ source row, naming the displayed completion datum and its finite functorial handoff;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger used to state all precision requests;
\item $W$ is the $\StreamNameUp$ window row that exposes the finite prefixes inspected at each tolerance;
\item $R$ is the $\RegSeqRatUp$ readback row supplying regular rational approximants for those windows;
\item $M$ is the modulus row, recording that a dyadic tolerance request selects a displayed finite window before the completion-facing read is exported;
\item $E$ is the terminal $\RealUp$ seal row reached from the regular rational readback and the modulus ledger;
\item $H$ records componentwise $\hsame$ transport for $F,D,W,R,M,E$;
\item $C$ records displayed $\Cont$ replay from the uniform completion datum through the dyadic, stream, regular, modulus, and real-seal rows;
\item $P$ is the $\Pkg$ provenance over $\UniformCauchyCompletionRealizerUp$, $\UniformCompletionFunctorUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\UniformCauchyCompletionRealizerUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient completion equality, a selected limit point, a host complete metric space, countable choice, or an ambient completeness theorem for $\RealUp$.
\end{definition}

\begin{theorem}[UniformCauchyCompletionRealizer NameCert obligations]
\label{thm:uniform-cauchy-completion-realizer-namecert-obligations}
For every accepted $\UniformCauchyCompletionRealizerUp$ carrier
$$
U=(F,D,W,R,M,E,H,C,P,N),
$$
the local $\NameCert_{\UniformCauchyCompletionRealizerUp}$ surface consists exactly of carrier admission for $U$, uniform completion datum exposure through $F$, dyadic tolerance visibility through $D$, finite stream-window visibility through $W$, regular rational readback through $R$, modulus selection through $M$, terminal $\RealUp$ seal readback through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.

Every completion-facing consumer must therefore read the displayed finite rows before it can use the realizer as a Real-facing output.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:uniform-cauchy-completion-realizer-carrier}. The packet displays the rows $F,D,W,R,M,E,H,C,P,N$, and each row has a fixed local role in the carrier.

Read the analytic route first. The row $F$ supplies the uniform completion datum, $D$ states dyadic precision, $W$ exposes the finite stream window requested by that precision, $R$ supplies the regular rational readback, $M$ records the modulus selecting the window, and $E$ is the resulting Real seal.

The support rows do not add analytic content. Componentwise $\hsame$ transport preserves the same displayed rows, $\Cont$ replay keeps their inspection order, $\Pkg$ records the cited sibling provenance, and $N$ names the local certificate. Since the carrier contains no additional coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[UniformCauchyCompletionRealizer modulus stability]
\label{thm:uniform-cauchy-completion-realizer-modulus-stability}
Let $U=(F,D,W,R,M,E,H,C,P,N)$ and $U'=(F',D',W',R',M',E',H',C',P',N')$ be accepted $\UniformCauchyCompletionRealizerUp$ carriers. If the dyadic tolerance rows $D,D'$, stream-window rows $W,W'$, regular readback rows $R,R'$, and modulus rows $M,M'$ agree under the displayed componentwise $\hsame$ transport, then every completion-facing consumer reads the same finite modulus route before reaching the terminal $\RealUp$ seal.

In particular, transport cannot replace the displayed modulus by a selected limit, a quotient-completion equality, or a host completeness argument.
\end{theorem}
\begin{proof}
Begin with the rows controlled by the hypothesis. Agreement of $D,D'$ fixes the dyadic precision ledger, agreement of $W,W'$ fixes the finite windows, agreement of $R,R'$ fixes the regular rational readbacks, and agreement of $M,M'$ fixes the modulus row that sends each precision request to its displayed window.

Apply componentwise transport through $H$ and $H'$. These rows preserve the analytic coordinates already named and do not introduce a new completion object or a selector for limits.

Finally replay the route through $C$ and $C'$. A completion-facing consumer reaches $E$ or $E'$ only after the same tolerance, window, readback, and modulus rows have been inspected. Therefore the consumer sees the same finite modulus route, and the excluded quotient, selection, host-space, and completeness readings remain outside the packet.
\end{proof}

\begin{theorem}[UniformCauchyCompletionRealizer Real-seal handoff]
\label{thm:uniform-cauchy-completion-realizer-real-seal-handoff}
Every $\RealUp$ consumer of an accepted $\UniformCauchyCompletionRealizerUp$ carrier
$$
U=(F,D,W,R,M,E,H,C,P,N)
$$
reaches the terminal seal $E$ only through the route
$$
F \longmapsto D \longmapsto W \longmapsto R \longmapsto M \longmapsto E
$$
and then through the structural rows $H,C,P,N$. The handoff exports a finite Real-facing seal from the uniform completion datum; it exports no selected limit, no quotient completion equality, no host complete-space object, no choice principle, and no ambient completeness theorem for $\RealUp$.
\end{theorem}
\begin{proof}
Read the carrier rows in their displayed order. The uniform completion datum $F$ is not itself a Real seal; it must first expose the dyadic tolerance row $D$, the finite stream window $W$, the regular rational readback $R$, and the modulus row $M$.

Only after those rows are visible does the consumer reach $E$. The continuation row $C$ records exactly this replay order, while $H$ preserves it under componentwise transport and $P,N$ package and name the same local surface.

The carrier definition supplies no coordinate for a host completed object, quotient equality of completion names, selected limit, countable-choice schedule, or ambient $\RealUp$ completeness. Hence the Real-facing output is precisely the displayed finite seal handoff.
\end{proof}

\closureat{UniformCauchyCompletionRealizerUp}{seedStr}

\begin{closurestatus}{\UniformCauchyCompletionRealizerUp}
  \constructivestory{A $\UniformCauchyCompletionRealizerUp$ packet is generated from uniform completion data, dyadic tolerance rows, finite stream windows, regular rational readback, a modulus row, a Real seal, componentwise hsame transport, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:uniform-cauchy-completion-realizer-carrier}, \autoref{thm:uniform-cauchy-completion-realizer-namecert-obligations}, \autoref{thm:uniform-cauchy-completion-realizer-modulus-stability}, and \autoref{thm:uniform-cauchy-completion-realizer-real-seal-handoff} bind the finite carrier, NameCert obligation surface, modulus stability, and Real-seal handoff for the L10 completion realizer route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close selected limits, quotient completion equality, host complete spaces, choice, or $\RealUp$ completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, modulus-row stability, Real-seal handoff coverage, and a Lean realization for BEDC.Derived.UniformCauchyCompletionRealizerUp.}
\end{closurestatus}
