\section{DiffForm root consumer factorization}
\label{sec:diffform-root-consumer-factorization}

\begin{definition}[DiffForm root consumer factorization surface]
\label{def:diffform-root-consumer-factorization-surface}
The $\DiffFormUp$ root consumer factorization surface is the tuple
$$
\mathsf{DiffFormRootConsumerFactor}_{M,T}.
$$
Its coordinates are the entry source of
\autoref{def:diffform-root-consumer-entry-source}, the carrier row of
\autoref{thm:diffform-root-consumer-entry-carrier}, the wedge row of
\autoref{thm:diffform-root-consumer-entry-wedge}, the exterior-derivative
row of \autoref{thm:diffform-root-consumer-entry-derivative}, and the
threshold row of \autoref{thm:diffform-root-consumer-entry-threshold}. The
surface is a consumer-facing route table, not a downstream law table: it
contains no row for $d^2=0$, closedness, nondegeneracy, contact
nonintegrability, quotienting, or a standard bridge.
\end{definition}

\begin{theorem}[DiffForm root carrier factorization]
\label{thm:diffform-root-consumer-factorization-carrier}
Every downstream carrier or classifier read from $\DiffFormUp$ factors
through \autoref{def:diffform-root-consumer-factorization-surface}. The only
carrier route is the root $BHist$ carrier
$\mathsf{DiffFormBHistCarrier}_{M,T}$, and the only classifier route is the
displayed $\sim_{\DiffFormUp}$ classifier bound by the root $BHist$ surface.
\end{theorem}
\begin{proof}
Start with an arbitrary carrier or classifier read by $\DeRhamUp$,
$\SymplecticUp$, or $\ContactUp$. Apply
\autoref{thm:diffform-root-bhist-downstream-boundary}. It places every
downstream read through the carried row, classifier row, degree-probe
alignment, wedge routing, exterior-input routing, source NameCert rows, and
$\Cont$ histories named by the root $BHist$ surface.

Now apply \autoref{thm:diffform-root-consumer-entry-carrier}. This entry row
identifies the consumer carrier coordinate with
$\mathsf{DiffFormBHistCarrier}_{M,T}$ and the consumer classifier coordinate
with the displayed $\sim_{\DiffFormUp}$ classifier, with no replacement
carrier or classifier.

Finally read these two coordinates inside
\autoref{def:diffform-root-consumer-factorization-surface}. Since the
factorization surface contains the entry source and the carrier entry row,
the downstream carrier and classifier read factors through exactly that
surface.
\end{proof}

\begin{theorem}[DiffForm wedge and derivative factorization]
\label{thm:diffform-root-consumer-factorization-wedge-derivative}
Every downstream wedge read or exterior-derivative input read from
$\DiffFormUp$ factors through
\autoref{def:diffform-root-consumer-factorization-surface}. Wedge reads use
the wedge-entry row, and exterior-derivative reads use the
exterior-derivative entry row; neither route projects a downstream law from
the $\DiffFormUp$ root.
\end{theorem}
\begin{proof}
First consider a downstream wedge read. Apply
\autoref{thm:diffform-root-consumer-entry-wedge}. It routes accepted wedge
input through probe append, $\Cont$ tensor and degree ledgers,
antisymmetry ledgers, scalar endpoint transport, and source-ledger
projections from the $\DiffFormUp$ root.

Next consider an exterior-derivative input read. Apply
\autoref{thm:diffform-root-consumer-entry-derivative}. It routes the input
through the manifold-tensor source envelope, supplying carrier, classifier,
degree-shift, wedge-input, endpoint-transport, source-ledger, and downstream
boundary data while leaving $d^2=0$ outside the root.

Finally apply
\autoref{thm:diffform-root-cross-consumer-threshold-package}. The package
assigns the de Rham, symplectic, and contact laws to their consumer faces and
keeps the shared carrier, classifier, wedge, scalar endpoint, and
source-ledger rows in the root face. Since
\autoref{def:diffform-root-consumer-factorization-surface} contains both
entry rows and the threshold row, every wedge or exterior-input read factors
through the shared surface.
\end{proof}

\begin{theorem}[DiffForm threshold consumer factorization]
\label{thm:diffform-root-consumer-factorization-threshold}
The three consumer faces $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$ may
cite only \autoref{def:diffform-root-consumer-factorization-surface} for
their shared $\DiffFormUp$ input. Nilpotence, closedness, nondegeneracy, and
contact nonintegrability must be supplied in the corresponding downstream
chapters and are not projected by the $\DiffFormUp$ root.
\end{theorem}
\begin{proof}
Begin with the shared input side. Apply
\autoref{thm:diffform-root-consumer-entry-threshold}. It assembles the
carrier, wedge, and exterior-derivative projections as the root entry
threshold for $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$.

Now apply
\autoref{thm:diffform-root-cross-consumer-threshold-package}. It separates
the shared root rows from the de Rham, symplectic, and contact law rows, so
consumer chapters receive only the common input surface from $\DiffFormUp$.

Finally apply \autoref{thm:diffform-root-bhist-downstream-boundary}. The root
$BHist$ boundary excludes $d^2=0$, closedness, nondegeneracy, contact
nonintegrability, and bridge rows from the $\DiffFormUp$ projection. Thus the
three consumer faces may cite the shared factorization surface for input, and
their own chapters must supply the corresponding downstream laws.
\end{proof}
