\begin{definition}[Differential-form downstream obligation inventory]
\label{def:diffform-downstream-obligation-inventory}
The downstream obligation inventory for $\DiffFormUp$ is the ten-field
boundary used when $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$ consume the
differential-form surface:
\begin{enumerate}
  \item traditional target: $\DiffFormUp$ as the boundary source for
  $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$;
  \item BEDC source: $BHist$, $\hsame$, $\Cont$,
  $\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
  $\NameCert_{\TensorProductUp}$;
  \item carrier: $\mathsf{DiffFormBHistCarrier}_{M,T}$;
  \item classifier: $\sim_{\DiffFormUp}$;
  \item stability obligations: carrier $\hsame$ transport, form classifier
  stability, scalar endpoint transport, and exterior-input classifier
  stability;
  \item ledger: only degree, probe, tensor, scalar, antisymmetry, and source
  rows may be projected;
  \item core theorem: the carrier, exterior-input, and consumer-boundary rows
  displayed in this file;
  \item exactness: row exhaustion of the displayed carrier and
  exterior-input packages;
  \item standard bridge: absent data;
  \item status: $\mathsf{ProofTarget}$.
\end{enumerate}
This inventory is a boundary statement. It supplies the rows that later
chapters may consume, and it does not assert $d^2=0$, closedness,
nondegeneracy, contact nonintegrability, or any standard bridge.
\end{definition}

\begin{theorem}[Differential-form downstream carrier-source obligation]
\label{thm:diffform-downstream-carrier-source-obligation}
Every downstream consumer of a $\DiffFormUp$ carrier row may project only the
six carrier coordinates
$$
(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)
$$
and the source scope
$$
BHist,\ \hsame,\ \Cont,\ \mathsf{ProbeBundle},\
\NameCert_{\ManifoldUp},\ \NameCert_{\TensorProductUp}.
$$
No $\DeRhamUp$, $\SymplecticUp$, or $\ContactUp$ consumer obtains an additional
carrier coordinate, hidden classifier, operator row, or geometric law from the
$\DiffFormUp$ carrier alone.
\end{theorem}
\begin{proof}
Project the carrier row by
\autoref{def:diffform-bhist-form-carrier}. A carried form is exactly the
six-tuple $(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)$, so the degree,
probe-bundle, tensor, scalar endpoint, antisymmetry, and source-ledger entries
are the full carrier surface.

Next apply \autoref{thm:diffform-source-scope}. The source ledger for any
accepted carrier row is restricted to $BHist$, $\hsame$, $\Cont$,
$\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
$\NameCert_{\TensorProductUp}$.

Combining the carrier projection with the source-scope projection exhausts
what a downstream consumer can read. Operator identities and geometric laws
are not carrier coordinates and are not named by the source ledger, so they
cannot be projected from the carrier alone.
\end{proof}

\begin{theorem}[Differential-form downstream exterior-input obligation]
\label{thm:diffform-downstream-exterior-input-obligation}
An accepted exterior-derivative input package exposes only the source carried
row, the output carried row, the one-step degree continuation ledger, the
probe transport ledger, the $\TensorProductUp$ tensor transport ledger, the
retained scalar endpoint transport, and the restricted source ledger. It
exposes no $d^2$ row, closedness row, nondegeneracy row, contact
nonintegrability row, or second-derivative law.
\end{theorem}
\begin{proof}
Unpack
\autoref{def:diffform-exterior-derivative-visible-input-package}. The package
lists the source and output carried rows, the unary degree histories, the
displayed one-step continuation $\Cont(d,\Eone(\emp),d^+)$, the probe
transport rows, the tensor row, the scalar endpoint comparison, and the
operator-owned source ledger.

Transport stability is exactly the row supplied by
\autoref{thm:diffform-exterior-derivative-input-classifier-stability}. It
keeps the package accepted under componentwise $\hsame$ transport and
preserves the retained scalar endpoint comparison as the scalar comparison of
the transported package.

The displayed list contains no row for $d^2$, closedness, nondegeneracy,
contact nonintegrability, or a second application of the exterior derivative.
By exhausting the visible package fields, those laws remain outside the
$\DiffFormUp$ exterior-input obligation.
\end{proof}

\begin{theorem}[Differential-form downstream consumer boundary]
\label{thm:diffform-downstream-consumer-boundary}
The chapters $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$ consume only the
displayed $\DiffFormUp$ carrier, source, and exterior-input rows of
\autoref{def:diffform-downstream-obligation-inventory}. Each such chapter must
supply its own operator law or geometric law: $d^2=0$ for de Rham structure,
closedness and nondegeneracy for symplectic structure, and contact
nonintegrability for contact structure.
\end{theorem}
\begin{proof}
First use
\autoref{thm:diffform-downstream-carrier-source-obligation}. It bounds every
carrier projection by the six displayed carrier coordinates and the six named
BEDC sources.

Next use \autoref{thm:diffform-downstream-exterior-input-obligation}. It
permits an exterior-derivative consumer to read the source and output carried
rows, one-step degree bookkeeping, probe and tensor transport, scalar endpoint
transport, and the restricted source ledger, but not $d^2$, closedness,
nondegeneracy, or contact nonintegrability.

Finally apply
\autoref{thm:diffform-exterior-derivative-downstream-scope}. That theorem
identifies $\DiffFormUp$ as the carrier, classifier, exterior-algebra
substrate, degree-raise candidate row, and endpoint-transport substrate for
$\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$. Composing it with the two
obligation rows above leaves exactly the displayed DiffForm rows available to
downstream consumers, so their operator and geometric laws must be supplied in
their own certificate surfaces.
\end{proof}
