\label{thm:diffform-wedge-degree-additivity-ledger}
Let
$$
\omega=(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)
$$
and
$$
\eta=(e,\mathcal{Q},\upsilon,\rho,\beta,\mu)
$$
be carried by $\mathsf{DiffFormBHistCarrier}_{M,T}$. If an admitted wedge row
$\omega\wedge_{\DiffFormUp}\eta$ is carried with output degree row $d\star e$,
then its visible degree ledger contains the unary continuation row
$\Cont(d,e,d\star e)$. If the two input form rows are transported by
componentwise classifier comparisons with degree rows $d'$ and $e'$ satisfying
$\hsame(d,d')$ and $\hsame(e,e')$, the wedge degree row is transported to a row
$d'\star e'$ classified with the same unary continuation/append degree
construction.
\end{theorem}
\begin{proof}
Start with the admitted wedge row and apply
\autoref{thm:diffform-wedge-ledger-coverage}. The wedge carrier contains the
visible tensor concatenation row joining the tensor component of $\omega$ to
the tensor component of $\eta$, and the carrier provenance records the degree
row of the wedge output.

The input degree rows are unary histories. Closure of unary histories under
continuation supplies the displayed degree ledger
$\Cont(d,e,d\star e)$ for the output degree row. This ledger is part of the
same BHist provenance that carries the wedge row, so it is visible to
downstream exterior-derivative consumers.

Now transport the two input form rows. The degree comparisons
$\hsame(d,d')$ and $\hsame(e,e')$ transport the two unary inputs, and the
componentwise classifier comparisons transport the probe, tensor, scalar, and
antisymmetry rows. Applying unary-history closure under the transported
continuation yields $d'\star e'$ with its corresponding $\Cont$ row.

Repackage the transported probe bundle, tensor concatenation, scalar endpoint,
antisymmetry ledger, and degree ledger as the wedge carrier row. The resulting
wedge row has degree additivity classified by the same differential-form
carrier and classifier surface.
\end{proof}

\begin{theorem}[Differential-form wedge ledger coverage]
\label{thm:diffform-wedge-ledger-coverage}
A wedge row $\omega\wedge_{\DiffFormUp}\eta$ is admitted by
$\mathsf{DiffFormBHistCarrier}_{M,T}$ only when its ledger visibly contains a
$\TensorProductUp$ concatenation row joining the tensor row of $\omega$ to the
tensor row of $\eta$. When that concatenation ledger is present, carrier and
classifier stability of the wedge row follow by transporting the two input
form rows through the tensor classifier and then through the retained scalar
classifier.
\end{theorem}
\begin{proof}
Read the wedge candidate through the carrier definition. The only provenance
accepted for a form row is its displayed ledger, and the tensor component of a
wedge must therefore be the visible tensor concatenation recorded there. If no
such $\TensorProductUp$ continuation row appears, the candidate has no accepted
carrier witness.

Assume the concatenation row is present. Transport the left and right form
rows by \autoref{thm:diffform-carrier-hsame-transport}. The
$\TensorProductUp$ source classifies the concatenated tensor endpoint after
the two input tensor rows have been transported, and the scalar endpoint is
classified by applying the retained scalar classifier to the transported
multilinear endpoints.

The antisymmetry ledger of the wedge is the concatenation of the two input
antisymmetry ledgers together with the displayed cross-permutation rows. Each
row is a visible BHist row, so $\hsame$ transport preserves it. These fields
reassemble into the carried wedge row and into the classifier comparison for
the transported wedge endpoints.
\end{proof}

\begin{definition}[Differential-form wedge probe concatenation ledger]
\label{def:diffform-wedge-probe-concatenation-ledger}
For carried form rows
$$
\omega=(d_\omega,\mathcal{P}_\omega,\tau_\omega,\sigma_\omega,\alpha_\omega,\lambda_\omega)
$$
and
$$
\eta=(d_\eta,\mathcal{P}_\eta,\tau_\eta,\sigma_\eta,\alpha_\eta,\lambda_\eta),
$$
the wedge probe concatenation ledger is the visible BHist package whose output
probe bundle is
$$
\mathcal{P}_{\omega\wedge\eta}
=\mathsf{bundleAppend}(\mathcal{P}_\omega,\mathcal{P}_\eta).
$$
It records the left input ledger $\lambda_\omega$, the right input ledger
$\lambda_\eta$, the two input $\mathsf{ProbeBundle}$ spines, the displayed
output $\mathsf{ProbeBundle}$ spine, and the same tensor-concatenation
provenance row used by the wedge ledger coverage of
\autoref{thm:diffform-wedge-ledger-coverage}.
\end{definition}

\begin{theorem}[Differential-form wedge probe concatenation coverage]
\label{thm:diffform-wedge-probe-concatenation-coverage}
Every wedge row $\omega\wedge_{\DiffFormUp}\eta$ admitted by
$\mathsf{DiffFormBHistCarrier}_{M,T}$ carries the wedge probe concatenation
ledger of \autoref{def:diffform-wedge-probe-concatenation-ledger}. Its output
probe bundle has length equal to the sum of the two input probe-bundle lengths,
and a probe row is in the output bundle exactly when it is in the left input
spine or in the right input spine.
\end{theorem}
\begin{proof}
Apply \autoref{thm:diffform-wedge-ledger-coverage}. The tensor concatenation
row in that ledger is read over the same two probe spines that occur in the
two carried input form rows, so the output probe surface is forced to be
$\mathsf{bundleAppend}(\mathcal{P}_\omega,\mathcal{P}_\eta)$.

Now induct on the left $\mathsf{ProbeBundle}$ spine. The empty case exposes
the right input spine as the whole output, giving the length and membership
claims directly from the right bundle.

In the cons case, the head probe remains the head of the output spine and the
induction hypothesis applies to the tail. Reassembling the head case with the
tail comparison gives length additivity for
$\mathsf{bundleAppend}$ and the membership iff splitting membership into the
left spine or the right spine.

The BHist row of
\autoref{def:diffform-wedge-probe-concatenation-ledger} stores exactly these
input ledgers, the output bundle, and the tensor provenance row. Therefore
every admitted wedge row carries the displayed probe concatenation surface.
\end{proof}

\begin{theorem}[Differential-form wedge probe concatenation classifier stability]
\label{thm:diffform-wedge-probe-concatenation-classifier-stability}
Let $(\omega,\eta)$ and $(\omega',\eta')$ be two pairs of carried
$\DiffFormUp$ rows with $\omega\sim_{\DiffFormUp}\omega'$ and
$\eta\sim_{\DiffFormUp}\eta'$. If their wedge rows are admitted, then the
wedge probe concatenation ledgers of
\autoref{def:diffform-wedge-probe-concatenation-ledger} are related by
$\hsame$, and the transported wedge outputs remain classified under
$\sim_{\DiffFormUp}$.
\end{theorem}
\begin{proof}
Use \autoref{thm:diffform-form-classifier-stability} to transport the two
input form classifiers componentwise. The probe-slot part of that transport is
controlled by \autoref{thm:diffform-probe-slot-arity-transport}, so the left
input probe bundles match and the right input probe bundles match with the
same visible arities.

Apply \autoref{thm:diffform-wedge-ledger-coverage} to the two admitted wedge
rows. Their tensor concatenation rows transport through the
$\TensorProductUp$ classifier, and the scalar endpoint rows transport through
the retained scalar classifier.

Finally transport the
$\mathsf{bundleAppend}(\mathcal{P}_\omega,\mathcal{P}_\eta)$ row
componentwise along the two input probe-bundle comparisons. The length and
membership clauses are preserved by
\autoref{thm:diffform-wedge-probe-concatenation-coverage}, and the left
ledger, right ledger, output probe bundle, and tensor provenance rows repack
as the required $\hsame$ comparison between the two probe concatenation
ledgers.
\end{proof}

\begin{definition}[Differential-form wedge associator ledger]
\label{def:diffform-wedge-associator-ledger}
For carried form rows $\omega$, $\eta$, and $\theta$ in
$\mathsf{DiffFormBHistCarrier}_{M,T}$, the visible wedge associator ledger is
the BHist package recording four rows: the $\TensorProductUp$ concatenation
spine for $(\omega\wedge_{\DiffFormUp}\eta)\wedge_{\DiffFormUp}\theta$, the
$\TensorProductUp$ concatenation spine for
$\omega\wedge_{\DiffFormUp}(\eta\wedge_{\DiffFormUp}\theta)$, the $\Cont$
associativity comparison between those tensor spines, and the common scalar
endpoint classifier obtained by transporting through the retained scalar
classifier. It also records the permutation-ledger comparison required to
identify the two antisymmetry ledgers after the tensor associativity
comparison has been applied.
\end{definition}

\begin{theorem}[Differential-form wedge associator closure]
\label{thm:diffform-wedge-associator-closure}
Let $\omega$, $\eta$, and $\theta$ be carried
$\mathsf{DiffFormBHistCarrier}_{M,T}$ rows. If the two binary wedge ledgers
needed for $(\omega\wedge_{\DiffFormUp}\eta)\wedge_{\DiffFormUp}\theta$ and
the two binary wedge ledgers needed for
$\omega\wedge_{\DiffFormUp}(\eta\wedge_{\DiffFormUp}\theta)$ are visible, then
the associator ledger of
\autoref{def:diffform-wedge-associator-ledger} carries both parenthesized
wedge rows and classifies them as equal under $\sim_{\DiffFormUp}$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:diffform-wedge-ledger-coverage} to
$\omega\wedge_{\DiffFormUp}\eta$ and then to the wedge with $\theta$. This
constructs the left-parenthesized carrier row and its scalar endpoint
classifier from the two visible binary ledgers.

Apply the same theorem to $\eta\wedge_{\DiffFormUp}\theta$ and then to the
wedge with $\omega$. This constructs the right-parenthesized carrier row and
its scalar endpoint classifier from the other two visible binary ledgers.

The two tensor endpoints are compared by the $\Cont$ associativity row in the
visible $\TensorProductUp$ concatenation ledger. Transport the scalar endpoint
classifier across that comparison and the retained scalar classifier from
\autoref{def:diffform-bhist-form-classifier}.

It remains to identify the antisymmetry ledgers. The associator ledger carries
the required permutation comparison, and each permutation row is a visible
BHist row. Composing those rows by $\hsame$ transitivity gives the
$\DiffFormUp$ classifier equality between the two parenthesized wedge rows.
\end{proof}

\begin{theorem}[Differential-form exterior-algebra obligation surface]
\label{thm:diffform-exterior-algebra-obligation-surface}
The $\DiffFormUp$ exterior-algebra surface available to $\DeRhamUp$,
$\SymplecticUp$, and $\ContactUp$ consists of carrier transport, classifier
stability, binary wedge ledger coverage, wedge probe concatenation coverage,
the wedge associator ledger, and the wedge degree ledger. This surface does
not assert $d^2=0$, closedness, nondegeneracy, or contact nonintegrability.
\end{theorem}
\begin{proof}
Carrier transport and classifier stability are supplied by
\autoref{thm:diffform-carrier-hsame-transport} and
\autoref{thm:diffform-form-classifier-stability}. Binary wedge admission and
transport are exactly \autoref{thm:diffform-wedge-ledger-coverage}, while the
visible output probe spine is the probe concatenation ledger of
\autoref{def:diffform-wedge-probe-concatenation-ledger} with coverage and
classifier stability from
\autoref{thm:diffform-wedge-probe-concatenation-coverage} and
\autoref{thm:diffform-wedge-probe-concatenation-classifier-stability}.

Associativity of the exposed exterior product is not an unrecorded algebraic
law. It is the visible associator ledger of
\autoref{def:diffform-wedge-associator-ledger}, closed under the carrier and
classifier by \autoref{thm:diffform-wedge-associator-closure}. Degree
bookkeeping is the visible unary-history ledger of
\autoref{def:diffform-wedge-degree-ledger}.

Combining these rows with the NameCert surface of
\autoref{thm:diffform-namecert-obligation-surface} and the downstream scope
of \autoref{thm:diffform-exterior-derivative-downstream-scope} gives exactly
the surface available to de Rham, symplectic, and contact consumers. The
operator identity $d^2=0$ and the geometric conditions named in the statement
are not rows of this $\DiffFormUp$ surface, so they remain obligations of the
downstream certificates that use it.
\end{proof}
