\begin{definition}[Differential-form admissible root row]
\label{def:diffform-admissible-root-row}
For fixed sources $\NameCert_{\ManifoldUp}$ and
$\NameCert_{\TensorProductUp}$, an admissible $\DiffFormUp$ root row is exactly
the visible BEDC tuple
$$
(BHist,\hsame,\Cont,\mathsf{ProbeBundle},
\NameCert_{\ManifoldUp},\NameCert_{\TensorProductUp},
\mathsf{Carr},\mathsf{Class},\mathsf{Wedge},\mathsf{Der})
$$
where $\mathsf{Carr}$ is the carrier row of
\autoref{def:diffform-bhist-form-carrier}, $\mathsf{Class}$ is the classifier
row of \autoref{def:diffform-bhist-form-classifier}, $\mathsf{Wedge}$ is the
visible family consisting of \autoref{thm:diffform-wedge-ledger-coverage},
\autoref{def:diffform-wedge-probe-concatenation-ledger},
\autoref{def:diffform-wedge-associator-ledger}, and
\autoref{def:diffform-wedge-degree-ledger}, and $\mathsf{Der}$ is the
exterior-derivative input family consisting of
\autoref{def:diffform-exterior-derivative-candidate-row} and
\autoref{thm:diffform-exterior-derivative-input-output-ledger-exactness}.
No further carrier, classifier, closedness, nilpotence, nondegeneracy, contact
nonintegrability, or bridge row is part of the root row.
\end{definition}

\begin{theorem}[Differential-form root-row carrier scope]
\label{thm:diffform-root-row-carrier-scope}
Every admissible root row of \autoref{def:diffform-admissible-root-row}
exposes only the carried form rows of
\autoref{def:diffform-bhist-form-carrier}, the classifier rows of
\autoref{def:diffform-bhist-form-classifier}, and the source boundary of
\autoref{thm:diffform-source-scope} on its carrier side.
\end{theorem}
\begin{proof}
Unpack the root row. Its carrier coordinate is named as
$\mathsf{Carr}$ and is definitionally the row of
\autoref{def:diffform-bhist-form-carrier}; its classifier coordinate is
$\mathsf{Class}$ and is definitionally the row of
\autoref{def:diffform-bhist-form-classifier}.

Project the carried row through \autoref{thm:diffform-source-scope}. The only
structural sources available to the carrier and classifier are $BHist$,
$\hsame$, $\Cont$, $\mathsf{ProbeBundle}$,
$\NameCert_{\ManifoldUp}$, and $\NameCert_{\TensorProductUp}$.

The definition of the root row contains no second carrier slot and no
additional classifier slot. Hence every carrier-side read factors through the
two displayed definitions and the cited source boundary.
\end{proof}

\begin{theorem}[Differential-form root-row wedge scope]
\label{thm:diffform-root-row-wedge-scope}
Every wedge use admitted by \autoref{def:diffform-admissible-root-row} is
limited to \autoref{thm:diffform-wedge-ledger-coverage},
\autoref{def:diffform-wedge-probe-concatenation-ledger},
\autoref{def:diffform-wedge-associator-ledger}, and
\autoref{def:diffform-wedge-degree-ledger}.
\end{theorem}
\begin{proof}
Inspect the $\mathsf{Wedge}$ coordinate of the root row. It is declared as the
four displayed wedge rows and no operator law beyond those rows.

The coverage theorem supplies the admitted tensor concatenation surface. The
probe-concatenation ledger records the probe spine, the associator ledger
records parenthesized tensor transport, and the degree ledger records the
visible unary degree bookkeeping.

Since the root row has no other wedge coordinate, any downstream wedge read
must choose one of these four rows. A Leibniz rule, closedness row, or
nilpotence row is therefore not present in the $\DiffFormUp$ root surface.
\end{proof}

\begin{theorem}[Differential-form root-row derivative scope]
\label{thm:diffform-root-row-derivative-scope}
Every exterior-derivative input admitted by
\autoref{def:diffform-admissible-root-row} is one of the candidate rows of
\autoref{def:diffform-exterior-derivative-candidate-row} together with the
exactness rows of
\autoref{thm:diffform-exterior-derivative-input-output-ledger-exactness}.
\end{theorem}
\begin{proof}
Read the $\mathsf{Der}$ coordinate. It lists the candidate row definition and
the input-output ledger exactness theorem as the complete exterior-derivative
input family.

The candidate row supplies only the source carried row, target carried row,
degree entries, one-step continuation row, probe bundle, tensor row, scalar
endpoint, antisymmetry ledger, and source ledger. The exactness theorem then
states that accepted input-output use is exhausted by those visible rows.

No additional derivative law is declared in the root row. Thus a second
derivative identity, closedness assertion, or bridge comparison must come from
a consumer certificate rather than from $\DiffFormUp$.
\end{proof}

\begin{theorem}[Differential-form root-row downstream boundary]
\label{thm:diffform-root-row-downstream-boundary}
The chapters $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$ may consume the
$\DiffFormUp$ surface only through the admissible root row of
\autoref{def:diffform-admissible-root-row}. They must supply closedness,
nondegeneracy, and contact nonintegrability in their own certificates.
\end{theorem}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormRootRow\_downstream\_boundary}
\begin{proof}
Combine the three scope projections above. The carrier projection gives only
the carrier, classifier, and source rows; the wedge projection gives only the
four wedge ledgers; the derivative projection gives only the candidate rows
and input-output exactness rows.

A $\DeRhamUp$ consumer may therefore read the displayed exterior-derivative
input family, but it receives no $d^2=0$ or closedness row. A
$\SymplecticUp$ consumer may read carried forms and wedge ledgers, but it
receives no nondegeneracy row.

A $\ContactUp$ consumer may read the same carrier, wedge, and derivative
surface, but it receives no contact nonintegrability row. These three
geometric obligations are not coordinates of the admissible root row, so each
must be certified on the consuming surface itself.
\end{proof}
