\begin{definition}[Differential-form exterior-derivative candidate row]
\label{def:diffform-exterior-derivative-candidate-row}
Fix carried rows $\omega$ and $\eta$ of
$\mathsf{DiffFormBHistCarrier}_{M,T}$. A differential-form
exterior-derivative candidate row $D(\omega,\eta)$ is an accepted visible
BHist package consisting exactly of the following data:
\begin{enumerate}
  \item the input carrier row $\omega$ and the output carrier row $\eta$;
  \item the unary input degree row $d_\omega$, the unary output degree row
  $d_\eta$, and the displayed one-step degree-raise ledger
  $\Cont(d_\omega,\mathsf{one},d_\eta)$;
  \item the transported tangent-probe bundle ledger from $\omega$ to $\eta$;
  \item the transported $\TensorProductUp$ multilinear row ledger from the
  input tensor row to the output tensor row;
  \item the transported scalar endpoint ledger classified by the retained
  scalar classifier of the manifold and tensor sources;
  \item a source ledger naming only $BHist$, $\hsame$, $\Cont$,
  $\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
  $\NameCert_{\TensorProductUp}$ as admissible sources for the displayed
  input-output package.
\end{enumerate}
This row is only the input-output surface for an exterior derivative supplied
by a downstream certificate. It does not assert $d^2=0$, closedness,
nondegeneracy, contact nonintegrability, or any second-derivative identity.
\end{definition}

\begin{theorem}[Differential-form exterior-derivative input-output ledger exactness]
\label{thm:diffform-exterior-derivative-input-output-ledger-exactness}
Every accepted $D(\omega,\eta)$ exposes exactly the input form row, the output
form row, the degree-raise $\Cont$ ledger, the probe transport ledger, the
$\TensorProductUp$ transport ledger, the scalar endpoint transport ledger,
and the source ledger listed in
\autoref{def:diffform-exterior-derivative-candidate-row}. No closedness,
nondegeneracy, contact condition, or second-derivative identity can be
projected from such a row.
\end{theorem}
\begin{proof}
Unfold \autoref{def:diffform-exterior-derivative-candidate-row}. The first
two displayed fields are carried $\mathsf{DiffFormBHistCarrier}_{M,T}$ rows,
and their carrier status is the same visible status transported by
\autoref{thm:diffform-carrier-hsame-transport}.

The output classifier is read only through
\autoref{thm:diffform-form-classifier-stability}. The scalar endpoint entry is
one of the displayed transport ledgers, so its admissible comparison is
exactly the scalar endpoint transport of
\autoref{thm:diffform-scalar-endpoint-transport}.

The remaining provenance is the source ledger. By
\autoref{thm:diffform-source-scope}, that ledger is restricted to $BHist$,
$\hsame$, $\Cont$, $\mathsf{ProbeBundle}$,
$\NameCert_{\ManifoldUp}$, and $\NameCert_{\TensorProductUp}$. These are the
only fields displayed by the candidate row, so exhausting the list gives the
claimed input-output ledger surface and leaves the excluded geometric and
operator identities unavailable.
\end{proof}

\begin{theorem}[Differential-form exterior-derivative candidate classifier transport]
\label{thm:diffform-exterior-derivative-candidate-classifier-transport}
Let $D(\omega,\eta)$ be an accepted exterior-derivative candidate row. Suppose
$\omega'$ is related to $\omega$ by $\sim_{\DiffFormUp}$, and suppose every
displayed degree, probe, tensor, scalar, and source ledger of
$D(\omega,\eta)$ is transported componentwise by $\hsame$ and by the retained
source classifiers named in the candidate source ledger. Then the transported
output row $\eta'$ is related to $\eta$ by $\sim_{\DiffFormUp}$, and the
transported package $D(\omega',\eta')$ is again an accepted
exterior-derivative candidate row.
\end{theorem}
\begin{proof}
Transport the input and output carrier rows through
\autoref{thm:diffform-carrier-hsame-transport}. The hypothesis gives the
componentwise $\hsame$ comparisons for the displayed degree, probe, tensor,
scalar, and source ledgers, and the source ledger permits only the retained
manifold and tensor classifiers for non-$\hsame$ endpoint comparisons.

The scalar endpoint clause is transported by
\autoref{thm:diffform-scalar-endpoint-transport}. The output form classifier
then follows from \autoref{thm:diffform-form-classifier-stability}, applied to
the transported degree, tensor, antisymmetry, scalar endpoint, and source
ledger fields of $\eta$ and $\eta'$.

It remains to rebuild the candidate row. Repack the transported input carrier,
transported output carrier, transported one-step degree-raise $\Cont$ ledger,
transported probe ledger, transported tensor ledger, transported scalar
endpoint ledger, and the same restricted source ledger. This is exactly the
field list of \autoref{def:diffform-exterior-derivative-candidate-row}, so
$D(\omega',\eta')$ is accepted.
\end{proof}

\begin{definition}[Differential-form exterior-derivative visible input package]
\label{def:diffform-exterior-derivative-visible-input-package}
Let
$$
\omega=(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)
$$
be a source row carried by $\mathsf{DiffFormBHistCarrier}_{M,T}$, and let
$$
D\omega=(d^+,\mathcal{P}^+,\tau^+,\sigma^+,\alpha^+,\lambda^+)
$$
be a carried output candidate. The package
$\mathsf{DiffFormExteriorInput}_{M,T}(\omega,D\omega)$ is accepted exactly
when its visible provenance consists of the two displayed $\DiffFormUp$
carrier rows, the unary degree rows $\mathsf{UnaryHistory}(d)$ and
$\mathsf{UnaryHistory}(d^+)$, the degree-raising continuation row
$$
\Cont(d,\Eone(\emp),d^+),
$$
the transported $\mathsf{ProbeBundle}$ rows connecting $\mathcal{P}$ with
$\mathcal{P}^+$, the retained $\TensorProductUp$ tensor row for the
multilinear output candidate, the retained scalar classifier comparison
between the source and output scalar endpoints, and the operator-owned source
ledger recording that these rows are the only inputs supplied to the
exterior-derivative construction. The package asserts no row for $d^2=0$,
closedness, nondegeneracy, or contact nonintegrability.
\end{definition}

\begin{theorem}[Differential-form exterior-derivative degree successor ledger]
\label{thm:diffform-exterior-derivative-degree-successor-ledger}
Every package accepted by
$\mathsf{DiffFormExteriorInput}_{M,T}(\omega,D\omega)$ exposes the source
degree row $\mathsf{UnaryHistory}(d)$, the output degree row
$\mathsf{UnaryHistory}(d^+)$, and the visible successor continuation row
$$
\Cont(d,\Eone(\emp),d^+).
$$
These are the only degree rows made available to a downstream
exterior-derivative consumer by the package.
\end{theorem}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormExteriorDerivativeLedger\_degree\_successor\_nonempty}
\begin{proof}
Unpack the accepted package of
\autoref{def:diffform-exterior-derivative-visible-input-package}. Its degree
fields are listed as the two unary-history rows and the displayed
$\Cont(d,\Eone(\emp),d^+)$ row.

The source and output are carried rows of
\autoref{def:diffform-bhist-form-carrier}, so their degree components are
visible BHist carrier entries rather than hidden operator data. Applying the
source-scope boundary of \autoref{thm:diffform-source-scope} shows that no
other degree provenance may be imported through this package.
\end{proof}

\begin{theorem}[Differential-form exterior-derivative input classifier stability]
\label{thm:diffform-exterior-derivative-input-classifier-stability}
Let $\mathsf{DiffFormExteriorInput}_{M,T}(\omega,D\omega)$ be accepted. If
the source and output carrier rows are transported componentwise by $\hsame$
to $\omega'$ and $D\omega'$, then
$\mathsf{DiffFormExteriorInput}_{M,T}(\omega',D\omega')$ is accepted. Under
the same transport, the retained scalar endpoint comparison between the
source and output scalar endpoints remains the scalar comparison carried by
the transported package.
\end{theorem}
\begin{proof}
First transport the two carrier rows. By
\autoref{thm:diffform-carrier-hsame-transport}, the transported source
$\omega'$ and transported output $D\omega'$ remain accepted
$\DiffFormUp$ carrier rows.

Next transport the classifier data. Apply
\autoref{thm:diffform-form-classifier-stability} to the componentwise
$\hsame$ comparisons of the two carrier rows. The degree rows, probe bundles,
tensor rows, antisymmetry ledgers, and operator-owned source ledger remain the
same visible rows up to $\hsame$, and the successor continuation row
$\Cont(d,\Eone(\emp),d^+)$ transports to the corresponding continuation row
for the transported degree endpoints.

Finally, apply \autoref{thm:diffform-scalar-endpoint-transport}. The retained
scalar endpoint comparison in the accepted package is preserved by the same
componentwise transport, so the transported rows reassemble as
$\mathsf{DiffFormExteriorInput}_{M,T}(\omega',D\omega')$ with its scalar
comparison still visible.
\end{proof}
