\begin{theorem}[Differential-form derived antisymmetry normal form]
\label{thm:diffform-derived-antisymmetry-normal-form}
Every finite permutation comparison admitted for carried $\DiffFormUp$ rows
over the same degree row factors through the differential-form antisymmetry
chain ledger of \autoref{def:diffform-antisymmetry-chain-ledger}. Each step of
the factorization is a visible adjacent swap, reverse rows are supplied by
\autoref{thm:diffform-adjacent-swap-involution-ledger}, and any transported
comparison remains a $\DiffFormUp$ classifier comparison by
\autoref{thm:diffform-antisymmetry-chain-classifier-stability}.
\end{theorem}
\begin{proof}
Begin with the carried rows in
\autoref{def:diffform-bhist-form-carrier}. Their permutation data are not an
external oracle: the carrier exposes only the antisymmetry ledger and the source
ledger, so any admitted comparison must be read as a displayed finite spine of
probe-bundle rows.

Apply \autoref{def:diffform-antisymmetry-chain-ledger} to identify this spine
as adjacent swaps over the carried $\mathsf{ProbeBundle}$ rows. For each step,
\autoref{thm:diffform-adjacent-swap-involution-ledger} supplies the reverse row
and the scalar endpoint comparison needed to return along the same visible
data.

Finally transport the comparison componentwise. The stability theorem
\autoref{thm:diffform-antisymmetry-chain-classifier-stability} carries the
degree, probe, tensor, scalar endpoint, antisymmetry, and source rows to the
transported carrier rows, so the derived comparison remains internal to
$\sim_{\DiffFormUp}$.
\end{proof}

\begin{theorem}[Differential-form de Rham boundary consumption]
\label{thm:diffform-derham-boundary-consumption}
A downstream $\DeRhamUp$ exterior-derivative row can consume $\DiffFormUp$ only
through the carried form rows, their classifier rows, wedge ledger coverage,
the wedge degree ledger, exterior-derivative candidate and input rows, scalar
endpoint transport, and the antisymmetry normal form of
\autoref{thm:diffform-derived-antisymmetry-normal-form}. It cannot read
$d^2=0$, closedness, nondegeneracy, or contact nonintegrability from
$\DiffFormUp$.
\end{theorem}
\begin{proof}
The carrier and classifier entries are exactly the displayed
$\mathsf{DiffFormBHistCarrier}_{M,T}$ and $\sim_{\DiffFormUp}$ rows. Wedge
admission is bounded by \autoref{thm:diffform-wedge-ledger-coverage}, and its
degree bookkeeping is the ledger of
\autoref{def:diffform-wedge-degree-ledger}.

The exterior-derivative interface is bounded by
\autoref{thm:diffform-derham-input-boundary} and
\autoref{thm:diffform-exterior-derivative-downstream-scope}. These theorems
list the visible candidate rows, input rows, probe/tensor/scalar transport
rows, and source ledgers available to a consumer.

It remains to control permutation comparisons inside the same boundary.
Apply \autoref{thm:diffform-derived-antisymmetry-normal-form}: every admitted
comparison is decomposed into the chain ledger, adjacent-swap reverse rows, and
classifier-stable transported rows.

None of these cited rows contains an operator-square identity, a closedness
predicate, a nondegeneracy predicate, or a contact nonintegrability predicate.
Those obligations therefore must be stated by the consuming $\DeRhamUp$,
$\SymplecticUp$, or $\ContactUp$ surface rather than read from $\DiffFormUp$.
\end{proof}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormAntisymmetryBoundary\_derham\_consumption\_separation}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormExteriorDerivativeLedger\_classifier\_transport\_nonempty\_boundary}

\begin{theorem}[Differential-form wedge derivative input boundary]
\label{thm:diffform-wedge-derivative-input-boundary}
When the same carried form appears both in a wedge row and in an
exterior-derivative input package, the shared visible data are exactly the
unary degree row, the wedge degree continuation ledger, the one-step derivative
continuation ledger, the probe, tensor, and scalar transport rows, and the
source ledger. No Leibniz rule and no nilpotence row are supplied by this
shared boundary.
\end{theorem}
\begin{proof}
Read the wedge side first. The available multiplicative data are the tensor
coverage theorem \autoref{thm:diffform-wedge-ledger-coverage} and the unary
degree continuation ledger of
\autoref{def:diffform-wedge-degree-ledger}; both are rows over the same carried
degree, probe, tensor, scalar endpoint, and source entries.

Read the exterior-derivative side through
\autoref{thm:diffform-derham-input-boundary} and
\autoref{thm:diffform-exterior-derivative-downstream-scope}. These rows expose
the derivative candidate, the one-step degree continuation, and the transport
clauses for the probe bundle, tensor row, scalar endpoint, and source ledger.

The intersection of the two readings is therefore the visible carrier data
they both name. Antisymmetry comparisons inside that intersection are governed
by \autoref{thm:diffform-derived-antisymmetry-normal-form}, so even transported
permutation data stay ledger-based.

A Leibniz rule would relate a derivative of a wedge to a sum of two derivative
terms, and nilpotence would relate two derivative steps. Neither row is among
the wedge coverage, wedge degree, exterior-derivative input, transport, or
source-ledger rows listed above, so the shared boundary supplies neither one.
\end{proof}
