\begin{definition}[Differential-form root consumer face classifier]
\label{def:diffform-root-consumer-face-classifier}
Fix the root export threshold source of
\autoref{def:diffform-root-export-threshold-source}. Its consumer face
classifier partitions the exported rows into three consumer faces and one
shared root face.
\begin{enumerate}
  \item The $\DeRhamUp$ face contains the exterior-derivative candidate and
  input rows, the one-step degree-shift row, the wedge-input stability row, and
  the downstream exterior-derivative scope row.
  \item The $\SymplecticUp$ face contains the carried form rows, wedge ledgers,
  antisymmetry ledgers, scalar endpoint rows, and Manifold/TensorProduct source
  ledgers needed to state a symplectic input surface. It excludes closedness and
  nondegeneracy.
  \item The $\ContactUp$ face contains the same carried-form, wedge-ledger, and
  derivative-input surface needed to state contact data. It excludes contact
  nonintegrability.
  \item The shared root face consists only of the six-coordinate $BHist$
  carrier, the displayed $\DiffFormUp$ classifier, wedge ledger rows, scalar
  endpoint rows, and the $\ManifoldUp/\TensorProductUp$ source ledgers.
\end{enumerate}
Rows not named in these four clauses are not exported from the
$\DiffFormUp$ root threshold.
\end{definition}

\begin{theorem}[Differential-form root consumer face coverage]
\label{thm:diffform-root-consumer-face-coverage}
Every row exported by \autoref{def:diffform-root-export-threshold-source} to
$\DeRhamUp$, $\SymplecticUp$, or $\ContactUp$ belongs to exactly one of the
three consumer faces of
\autoref{def:diffform-root-consumer-face-classifier}, or to the explicitly
shared root face. No exported row lies outside those four faces.
\end{theorem}
\begin{proof}
Project the exported root table with
\autoref{thm:diffform-root-export-namecert-threshold}. It lists the complete
threshold surface as the six-coordinate carrier, the displayed classifier,
wedge ledgers, the exterior-derivative input boundary, and the downstream
consumer separation.

Next apply \autoref{thm:diffform-downstream-consumer-boundary}. The de Rham
consumer receives the exterior-input and degree-shift surface, while the
symplectic and contact consumers receive the carried form, wedge, antisymmetry,
scalar endpoint, and source-ledger surface needed to state their own data.

Finally apply
\autoref{thm:diffform-boundary-exhaustion-downstream-export}. The
exhaustion statement says every downstream row is one of the displayed carrier,
classifier, wedge, antisymmetry, exterior-input, transport, source-ledger, or
downstream rows. Matching these rows against the four clauses of
\autoref{def:diffform-root-consumer-face-classifier} gives coverage, and the
last sentence of that definition excludes any fifth face.
\end{proof}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormRootConsumerFace\_coverage}

\begin{theorem}[Differential-form root consumer face disjointness]
\label{thm:diffform-root-consumer-face-disjointness}
The consumer-specific laws separated by the
\autoref{def:diffform-root-consumer-face-classifier} are disjoint:
nilpotence remains $\DeRhamUp$-specific, closedness and nondegeneracy remain
$\SymplecticUp$-specific, and contact nonintegrability remains
$\ContactUp$-specific. Only carried $BHist$ rows, classifier rows, wedge
ledgers, scalar endpoint rows, and source ledgers may be shared across
consumer faces.
\end{theorem}
\begin{proof}
Start from \autoref{thm:diffform-root-export-downstream-law-separation}. It
states that the $\DiffFormUp$ root threshold exports no $d^2=0$, closedness,
nondegeneracy, or contact nonintegrability row. Those rows therefore cannot
belong to the shared root face.

Now use \autoref{thm:diffform-downstream-consumer-boundary}. That boundary
assigns $d^2=0$ to the de Rham certificate surface, closedness and
nondegeneracy to the symplectic certificate surface, and contact
nonintegrability to the contact certificate surface. Hence the laws themselves
are pairwise consumer-specific.

The rows allowed to cross consumer faces are exactly the displayed carrier,
classifier, wedge, scalar endpoint, and source-ledger rows named in the shared
root face of \autoref{def:diffform-root-consumer-face-classifier}. Since the
law rows are absent from the root export threshold, no consumer-specific law is
shared by the classifier.
\end{proof}
\leanchecked{BEDC.Derived.DiffFormUp.DiffFormRootConsumerFace\_disjointness}

\begin{theorem}[Differential-form root cross-consumer threshold package]
\label{thm:diffform-root-cross-consumer-threshold-package}
The definition
\autoref{def:diffform-root-consumer-face-classifier}, the coverage theorem
\autoref{thm:diffform-root-consumer-face-coverage}, and the disjointness
theorem \autoref{thm:diffform-root-consumer-face-disjointness} form the
cross-consumer root threshold package for the $\DiffFormUp$ surface consumed by
$\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$.
\end{theorem}
\begin{proof}
The classifier supplies the four faces: de Rham, symplectic, contact, and the
shared root face.

Coverage then shows that every exported downstream row is assigned to one of
those faces. Disjointness shows that the downstream laws remain outside the
shared root face and are owned by the corresponding consumer chapters.

Together these two properties make the root export threshold citable as a
single cross-consumer package: downstream chapters can reuse the shared root
rows without reading nilpotence, closedness, nondegeneracy, or contact
nonintegrability back into the $\DiffFormUp$ root.
\end{proof}
