\section{DiffForm root consumer export packet}
\label{sec:diffform-root-consumer-export-packet}

\begin{definition}[DiffForm root consumer export packet]
\label{def:diffform-root-consumer-export-packet}
The $\DiffFormUp$ root consumer export packet is the paper-side union
$$
\mathsf{DiffFormRootConsumerExport}_{M,T}.
$$
Its positive surface consists exactly of the root-unblock source surface of
\autoref{def:diffform-root-unblock-source-surface}, the carrier and
classifier scope theorem
\autoref{thm:diffform-root-unblock-carrier-classifier-scope}, the wedge and
$\Cont$ closure theorem
\autoref{thm:diffform-root-unblock-wedge-cont-closure}, the exterior-input
consumption theorem
\autoref{thm:diffform-root-unblock-derham-input-consumption}, the consumer
face classifier of \autoref{def:diffform-root-consumer-face-classifier}, the
face exhaustion theorem
\autoref{thm:diffform-root-consumer-face-exhaustion}, and the
consumer-readable package of
\autoref{def:diffform-root-consumer-readable-package} with its boundary
theorem \autoref{thm:diffform-root-consumer-namecert-boundary}. The packet
contains no row outside these cited root-unblock, face-classifier,
face-exhaustion, and readable-package surfaces.
\end{definition}

\begin{theorem}[DiffForm root consumer export coverage]
\label{thm:diffform-root-consumer-export-coverage}
Every $\DeRhamUp$, $\ContactUp$, or $\SymplecticUp$ consumer row admitted at
the $\DiffFormUp$ root factors through
\autoref{def:diffform-root-consumer-export-packet}.
\end{theorem}
\begin{proof}
Start with a consumer row admitted at the $\DiffFormUp$ root. By the source
surface in \autoref{def:diffform-root-unblock-source-surface}, such a row may
read only the displayed $BHist$, $\hsame$, $\Cont$, probe-bundle,
$\NameCert_{\ManifoldUp}$, $\NameCert_{\TensorProductUp}$, carrier,
classifier, wedge, and exterior-input coordinates.

Apply \autoref{thm:diffform-root-unblock-derham-input-consumption}. It
restricts $\DeRhamUp$, $\ContactUp$, and $\SymplecticUp$ consumers to the
degree, wedge, antisymmetry, scalar endpoint, and source-ledger rows exposed
by the root-unblock surface.

Now apply \autoref{thm:diffform-root-consumer-face-exhaustion}. Every row
exported by the root threshold is shared root data or belongs to exactly one
of the de Rham, symplectic, and contact faces.

Finally use
\autoref{thm:diffform-root-consumer-namecert-boundary}. The downstream
citation surface is the consumer-readable package named in
\autoref{def:diffform-root-consumer-export-packet}, so the admitted consumer
row factors through that packet and has no independent root route.
\end{proof}

\begin{theorem}[DiffForm root consumer export exactness]
\label{thm:diffform-root-consumer-export-exactness}
The packet
\autoref{def:diffform-root-consumer-export-packet} exposes exactly the
six-coordinate carrier, displayed classifier, wedge-continuation rows,
antisymmetry ledger, scalar endpoint row, source ledger, and exterior-input
rows named by the cited root-unblock and consumer-face surfaces.
\end{theorem}
\begin{proof}
Project the carrier and classifier coordinates with
\autoref{thm:diffform-root-unblock-carrier-classifier-scope}. The carrier is
the six-coordinate row
$$
(d,\mathcal{P},\tau,\sigma,\alpha,\lambda),
$$
and the classifier reads only the displayed degree, tensor, scalar endpoint,
antisymmetry, tensor-ledger, and source-ledger comparisons.

Next project the operation rows with
\autoref{thm:diffform-root-unblock-wedge-cont-closure}. Wedge admission reads
only probe append, the $\Cont$ tensor ledger, degree bookkeeping, and the
displayed antisymmetry ledger.

The exterior side is supplied by
\autoref{thm:diffform-root-unblock-derham-input-consumption}. It restricts
exterior consumers to degree, wedge, antisymmetry, scalar endpoint, and
source-ledger projections.

Finally use
\autoref{thm:diffform-root-consumer-face-exhaustion} and
\autoref{thm:diffform-root-consumer-namecert-boundary}. Face exhaustion says
there is no exported row beyond the shared root and three consumer faces, and
the readable boundary repacks the same carrier, classifier, stability, ledger,
wedge-routing, exterior-input, and source NameCert rows. Hence the packet is
exactly the stated export surface.
\end{proof}

\begin{theorem}[DiffForm root consumer export no extra laws]
\label{thm:diffform-root-consumer-export-no-extra-laws}
The packet
\autoref{def:diffform-root-consumer-export-packet} contains no $d^2=0$,
closedness, nondegeneracy, contact nonintegrability, or standard bridge row.
\end{theorem}
\begin{proof}
First inspect the defining source surface
\autoref{def:diffform-root-unblock-source-surface}. It explicitly contains no
row for $d^2=0$, closedness, nondegeneracy, contact nonintegrability, or a
standard bridge.

Apply \autoref{thm:diffform-root-unblock-derham-input-consumption}. The
theorem keeps de Rham nilpotence, symplectic closedness and nondegeneracy, and
contact nonintegrability in the downstream certificate surfaces.

Then apply \autoref{thm:diffform-root-consumer-face-exhaustion} together with
\autoref{thm:diffform-root-consumer-boundary-exactness}. Exhaustion assigns
every exported row to the shared root or a unique consumer face, while
boundary exactness excludes the downstream law rows and any standard bridge.

The readable package boundary
\autoref{thm:diffform-root-consumer-namecert-boundary} names the same
negative boundary. Therefore the export packet carries the root-unblocking
surface and no extra exterior or geometric law.
\end{proof}
