\begin{definition}[Differential-form root source obligation package]
\label{def:diffform-root-source-obligation-package}
The root source obligation package for $\DiffFormUp$ is the following
per-object template, read over the certificate section
\autoref{sec:diffform-certificate}.
\begin{enumerate}
  \item The traditional target is the differential-form surface of
  antisymmetric multilinear tangent probes equipped with wedge.
  \item The BEDC source language is $\mathsf{BHist}$, with comparison rows
  supplied by $\hsame$.
  \item Continuation rows are exactly the visible $\Cont$ rows attached to
  tensor concatenation, wedge degree bookkeeping, and the exported
  exterior-derivative input boundary.
  \item Probe data are finite $\mathsf{ProbeBundle}$ rows over the tangent
  source surface.
  \item The upstream certificate sources are
  $\NameCert_{\ManifoldUp}$ and $\NameCert_{\TensorProductUp}$.
  \item The carrier choice is
  $\mathsf{DiffFormBHistCarrier}_{M,T}$ of
  \autoref{def:diffform-bhist-form-carrier}.
  \item The classifier choice is $\sim_{\DiffFormUp}$ of
  \autoref{def:diffform-bhist-form-classifier}.
  \item Stability obligations are the carrier transport, classifier
  stability, wedge probe transport, wedge associator transport, wedge degree
  stability, antisymmetry transport, and exterior-derivative input transport
  rows already displayed in the chapter.
  \item The source ledger is the visible ledger over $BHist$, $\hsame$,
  $\Cont$, $\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
  $\NameCert_{\TensorProductUp}$.
  \item The core theorem list consists of carrier obligation, classifier
  obligation, ledger exactness, classifier reflexivity, wedge ledger
  coverage, wedge probe concatenation coverage, wedge associator closure,
  wedge degree stability, and the exported input-boundary statements.
  \item The exactness predicate is ledger exhaustion: every accepted root row
  is one of the displayed carrier, classifier, continuation, probe, upstream
  certificate, wedge, antisymmetry, or input-boundary rows.
  \item The standard bridge slot is absent, and the current status is a
  paper-side root obligation surface rather than a standard-object bridge.
\end{enumerate}
No closedness predicate, nondegeneracy predicate, contact predicate, or
$d^2=0$ row belongs to this root source package.
\end{definition}

\begin{theorem}[Differential-form root carrier source obligation]
\label{thm:diffform-root-carrier-source-obligation}
Every admitted root $\DiffFormUp$ row factors through the six displayed
carrier coordinates
$$
(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)
$$
of \autoref{def:diffform-bhist-form-carrier} and through the upstream
$\NameCert_{\ManifoldUp}$ and $\NameCert_{\TensorProductUp}$ certificate
rows. The root carrier has no host tangent-space carrier and no external
alternating-map carrier outside those displayed BEDC sources.
\end{theorem}
\begin{proof}
Unpack the carrier definition. A row accepted by
$\mathsf{DiffFormBHistCarrier}_{M,T}$ is presented by the six histories
$(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)$, and the acceptance clauses name
only degree, probe, tensor, scalar endpoint, antisymmetry, and source-ledger
data.

The probe coordinate is read through the tangent-source rows retained by
$\NameCert_{\ManifoldUp}$. The tensor and continuation coordinates are read
through $\NameCert_{\TensorProductUp}$, while the scalar endpoint classifier is
the scalar classifier retained by the same upstream sources.

Finally inspect the source ledger $\lambda$. It records the names $M$ and $T$
and the five visible carrier components already listed. Since no acceptance
clause constructs another carrier, a host tangent-space object or an external
alternating-map object has no entry point into the root row.
\end{proof}

\begin{theorem}[Differential-form root wedge operation obligation]
\label{thm:diffform-root-wedge-operation-obligation}
The wedge operation obligation for root $\DiffFormUp$ rows is exactly the
visible concatenation, degree-additivity, associator, and
classifier-stability ledger supplied by
\autoref{thm:diffform-wedge-ledger-coverage},
\autoref{def:diffform-wedge-probe-concatenation-ledger},
\autoref{thm:diffform-wedge-probe-concatenation-coverage},
\autoref{thm:diffform-wedge-probe-concatenation-classifier-stability},
\autoref{def:diffform-wedge-associator-ledger},
\autoref{thm:diffform-wedge-associator-closure},
\autoref{def:diffform-wedge-degree-ledger}, and
\autoref{thm:diffform-wedge-degree-classifier-stability}.
\end{theorem}
\begin{proof}
Read wedge admission first. The coverage theorem
\autoref{thm:diffform-wedge-ledger-coverage} bounds the operation by the two
input carrier rows, the concatenated tensor row, the output scalar endpoint,
the inherited antisymmetry data, and the displayed source ledger.

Next read the probe and degree ledgers. The probe spine is the visible
concatenation ledger of
\autoref{def:diffform-wedge-probe-concatenation-ledger}, with coverage and
classifier transport supplied by
\autoref{thm:diffform-wedge-probe-concatenation-coverage} and
\autoref{thm:diffform-wedge-probe-concatenation-classifier-stability}. The
degree row is the unary-history ledger of
\autoref{def:diffform-wedge-degree-ledger}, and its classifier transport is
\autoref{thm:diffform-wedge-degree-classifier-stability}.

It remains to account for parenthesizing. The associator data are exactly the
visible ledger of \autoref{def:diffform-wedge-associator-ledger}, and closure
under the carried classifier is supplied by
\autoref{thm:diffform-wedge-associator-closure}. These cited rows exhaust the
operation obligation, so no additional wedge source is being assumed.
\end{proof}

\begin{theorem}[Differential-form root source ledger obligation]
\label{thm:diffform-root-source-ledger-obligation}
All accepted source ledger entries for the root $\DiffFormUp$ package are
exhausted by $BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$,
$\NameCert_{\ManifoldUp}$, and $\NameCert_{\TensorProductUp}$ rows. No
standard bridge, closedness predicate, nondegeneracy predicate, contact
predicate, or $d^2=0$ row is part of the root obligation.
\end{theorem}
\begin{proof}
Begin with the root package of
\autoref{def:diffform-root-source-obligation-package}. Its source language,
comparison rows, continuation rows, probe rows, and upstream certificate rows
are explicitly listed as $BHist$, $\hsame$, $\Cont$,
$\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
$\NameCert_{\TensorProductUp}$.

The carrier and classifier definitions do not widen that list.
\autoref{def:diffform-bhist-form-carrier} exposes only the six carried
coordinates and their upstream sources, while
\autoref{def:diffform-bhist-form-classifier} uses only $\hsame$ and the
retained scalar classifier. The core ledger exactness statement
\autoref{thm:diffform-bhist-ledger-exactness-obligation} gives the same
exhaustion for the core certificate rows.

The remaining root operation rows are wedge rows. By
\autoref{thm:diffform-root-wedge-operation-obligation}, these are the visible
concatenation, degree, associator, and classifier-stability ledgers already
named above. None of those ledgers contains a standard bridge, a closedness
predicate, a nondegeneracy predicate, a contact predicate, or a two-step
exterior-derivative identity.
\end{proof}

\begin{definition}[Differential-form root obligation package]
\label{def:diffform-root-obligation-package}
The root obligation package for $\DiffFormUp$ is the displayed
$BHist$ package over $BHist$, $\hsame$, $\Cont$,
$\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
$\NameCert_{\TensorProductUp}$ whose public rows are the following four
surfaces.
\begin{enumerate}
\item The visible source surface is the carrier and classifier surface of
\autoref{def:diffform-bhist-form-carrier} and
\autoref{def:diffform-bhist-namecert-core-rows}, with no source outside the
six displayed inputs.
\item The antisymmetry ledger is the finite adjacent-swap chain surface of
\autoref{def:diffform-antisymmetry-chain-ledger}, transported through the
$\DiffFormUp$ classifier.
\item The wedge-probe ledger is the wedge degree, tensor-continuation, and
probe-concatenation surface carried by admitted wedge rows.
\item The downstream consumption row is the boundary through which
$\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$ may consume $\DiffFormUp$ data.
\end{enumerate}
The package exports no standard bridge and no geometric identity beyond these
listed rows.
\end{definition}

\begin{theorem}[Differential-form visible source surface obligation]
\label{thm:diffform-visible-source-surface-obligation}
The root obligation package of
\autoref{def:diffform-root-obligation-package} exposes no source beyond
$BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$,
$\NameCert_{\ManifoldUp}$, and $\NameCert_{\TensorProductUp}$. Its carrier,
classifier, and core ledger rows are exactly the rows of
\autoref{def:diffform-bhist-form-carrier},
\autoref{def:diffform-bhist-namecert-core-rows},
\autoref{thm:diffform-bhist-ledger-exactness-obligation}, and
\autoref{thm:diffform-source-scope}.
\end{theorem}
\begin{proof}
Read the carrier first. By \autoref{def:diffform-bhist-form-carrier}, a
carried form row consists of the degree history, probe bundle, tensor row,
scalar endpoint row, antisymmetry ledger, and source ledger. Each entry is a
visible row over the displayed $BHist$, $\mathsf{ProbeBundle}$,
$\Cont$, $\NameCert_{\ManifoldUp}$, or $\NameCert_{\TensorProductUp}$
surface.

The classifier and core rows introduce no further source. The core rows of
\autoref{def:diffform-bhist-namecert-core-rows} are exhausted by the
displayed carrier, classifier, transport, wedge, antisymmetry, and source
provenance clauses, and
\autoref{thm:diffform-bhist-ledger-exactness-obligation} states that every
accepted ledger row is visible BHist provenance.

Finally apply \autoref{thm:diffform-source-scope}. It identifies the source
boundary of every accepted row with the same six inputs named in the root
package. Hence the root package exposes the displayed kernel and upstream
NameCert rows, and nothing else.
\end{proof}

\begin{theorem}[Differential-form root antisymmetry ledger obligation]
\label{thm:diffform-root-antisymmetry-ledger-obligation}
In the root obligation package of
\autoref{def:diffform-root-obligation-package}, antisymmetry enters only
through the finite $\mathsf{ProbeBundle}$ permutation chain ledger of
\autoref{def:diffform-antisymmetry-chain-ledger}. Every admitted
antisymmetry comparison is covered by
\autoref{thm:diffform-antisymmetry-chain-coverage} and transports through the
$\DiffFormUp$ classifier by
\autoref{thm:diffform-antisymmetry-chain-classifier-stability}.
\end{theorem}
\begin{proof}
Locate the antisymmetry data inside the carried form row. The carrier has a
single antisymmetry ledger slot, and
\autoref{def:diffform-antisymmetry-chain-ledger} identifies its public
content as a finite spine of adjacent-swap rows over the carried
$\mathsf{ProbeBundle}$.

Apply \autoref{thm:diffform-antisymmetry-chain-coverage}. The theorem
exhausts an admitted finite permutation comparison by the displayed adjacent
swaps and their scalar endpoint rows. No permutation oracle or hidden
classifier clause is available outside that ledger.

It remains to check transport. By
\autoref{thm:diffform-antisymmetry-chain-classifier-stability}, componentwise
$\hsame$ transport of the carried rows transports the finite chain ledger and
reassembles the transported endpoints as a $\DiffFormUp$ classifier
comparison. Thus the root package treats antisymmetry only as visible ledger
data.
\end{proof}

\begin{theorem}[Differential-form root wedge-probe obligation]
\label{thm:diffform-root-wedge-probe-obligation}
Every wedge row exposed by the root obligation package of
\autoref{def:diffform-root-obligation-package} exposes precisely the degree
additivity ledger, probe concatenation ledger, tensor-continuation
provenance, and classifier stability rows supplied by
\autoref{thm:diffform-wedge-degree-additivity-ledger},
\autoref{thm:diffform-wedge-ledger-coverage},
\autoref{thm:diffform-wedge-probe-concatenation-coverage}, and
\autoref{thm:diffform-wedge-probe-concatenation-classifier-stability}.
\end{theorem}
\begin{proof}
Begin with an admitted wedge row. The coverage theorem
\autoref{thm:diffform-wedge-ledger-coverage} requires a visible
$\TensorProductUp$ concatenation row joining the tensor component of the left
form to the tensor component of the right form. This is the tensor
continuation provenance available at the root boundary.

Next read the degree and probe rows. The degree additivity statement of
\autoref{thm:diffform-wedge-degree-additivity-ledger} records the unary
degree continuation for the wedge output. The probe coverage theorem
\autoref{thm:diffform-wedge-probe-concatenation-coverage} records the output
probe bundle as the append of the two input probe spines, with the visible
length and membership clauses.

Finally transport the row. The classifier stability theorem
\autoref{thm:diffform-wedge-probe-concatenation-classifier-stability}
transports the concatenated probe ledger together with the tensor and scalar
endpoint comparisons. These are exactly the wedge rows listed in the root
package, so no further multiplicative source is exposed.
\end{proof}

\begin{theorem}[Differential-form root downstream consumption obligation]
\label{thm:diffform-root-downstream-consumption-obligation}
The downstream consumers $\DeRhamUp$, $\SymplecticUp$, and $\ContactUp$
receive from the root obligation package of
\autoref{def:diffform-root-obligation-package} only the carried
$\DiffFormUp$ rows, classifier rows, wedge rows, antisymmetry rows, and
exterior-input boundary rows described by
\autoref{thm:diffform-exterior-derivative-downstream-scope},
\autoref{thm:diffform-derham-boundary-consumption},
\autoref{thm:diffform-wedge-derivative-input-boundary}, and
\autoref{thm:diffform-namecert-obligation-surface}. The identities $d^2=0$,
closedness, nondegeneracy, and contact nonintegrability remain obligations
of the consuming chapters.
\end{theorem}
\begin{proof}
Inspect the exported surface first.
\autoref{thm:diffform-namecert-obligation-surface} lists the carrier,
classifier, transport, wedge, antisymmetry, exterior-input, and downstream
scope rows that the $\DiffFormUp$ surface exports. This is the entire public
obligation surface of the root package.

Now apply the downstream boundary statements.
\autoref{thm:diffform-exterior-derivative-downstream-scope} bounds
exterior-derivative consumers to the degree row, probe bundle, tensor row,
scalar endpoint row, antisymmetry ledger, wedge ledgers, and
exterior-derivative candidate ledger.
\autoref{thm:diffform-derham-boundary-consumption} gives the same boundary
for $\DeRhamUp$ consumption, including the normal-form antisymmetry row.

The shared wedge and derivative input boundary is controlled by
\autoref{thm:diffform-wedge-derivative-input-boundary}. It permits only the
visible unary degree row, degree-continuation ledgers, probe, tensor, scalar,
and source rows common to the wedge and exterior-input readings.

None of the cited rows contains nilpotence, closedness, nondegeneracy, or
contact nonintegrability. Therefore those four facts are not imported from
$\DiffFormUp$; they must be supplied by the $\DeRhamUp$, $\SymplecticUp$, and
$\ContactUp$ chapters that use the root package.
\end{proof}
