\section{DiffForm root export threshold}
\label{sec:diffform-root-export-threshold}

\begin{definition}[Differential-form root export threshold source]
\label{def:diffform-root-export-threshold-source}
Fix the $\NameCert_{\ManifoldUp}$ source $M$ and the
$\NameCert_{\TensorProductUp}$ source $T$ used in
\autoref{def:diffform-bhist-form-carrier}. The root export threshold source
for $\DiffFormUp$ is the displayed row package consisting exactly of
$BHist$, $\hsame$, $\Cont$, $\mathsf{ProbeBundle}$,
$\NameCert_{\ManifoldUp}$, $\NameCert_{\TensorProductUp}$, the carrier and
classifier rows of \autoref{def:diffform-bhist-form-carrier} and
\autoref{def:diffform-bhist-form-classifier}, the wedge-ledger rows cited by
\autoref{thm:diffform-root-wedge-ledger-obligation}, the exterior-derivative
input boundary cited by \autoref{thm:diffform-root-exterior-boundary-obligation},
and the downstream-consumer boundary of
\autoref{thm:diffform-downstream-consumer-boundary}.

This threshold source is an export boundary. It names the rows that a
consumer may read from the $\DiffFormUp$ root surface, and it names no
nilpotence, closedness, nondegeneracy, contact nonintegrability, or standard
bridge row.
\end{definition}

\begin{theorem}[Differential-form carrier and classifier export threshold]
\label{thm:diffform-root-export-carrier-classifier-threshold}
At the threshold of \autoref{def:diffform-root-export-threshold-source}, the
exported carrier is exactly the six-coordinate row
$$
(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)
$$
of \autoref{def:diffform-bhist-form-carrier}. The exported classifier is only
the comparison of degree rows by $\hsame$, matched tensor and scalar endpoint
comparisons through the displayed source rows, and visible ledger comparisons
by $\hsame$ as stated in \autoref{def:diffform-bhist-form-classifier}. No
additional carrier coordinate, classifier, operator row, or geometric law is
exported at the root threshold.
\end{theorem}
\begin{proof}
Read the source boundary through
\autoref{thm:diffform-root-source-obligation}. That theorem restricts every
root row to the displayed $BHist$, $\hsame$, $\Cont$,
$\mathsf{ProbeBundle}$, $\NameCert_{\ManifoldUp}$, and
$\NameCert_{\TensorProductUp}$ sources, with no source row outside the six
carrier entries.

Project the carrier with \autoref{def:diffform-bhist-form-carrier}. The row
is the tuple $(d,\mathcal{P},\tau,\sigma,\alpha,\lambda)$, and each coordinate
is respectively the degree history, probe bundle, tensor row, scalar endpoint,
antisymmetry ledger, or source ledger. Therefore the export carrier has no
seventh coordinate.

Project the classifier with
\autoref{def:diffform-bhist-form-classifier}. Its degree clause is $\hsame$,
its tensor and scalar clauses compare matched displayed rows using the
retained source classifiers, and its remaining clauses are visible ledger
$\hsame$ comparisons. These are precisely the classifier rows permitted by the
threshold source.
\end{proof}

\begin{theorem}[Differential-form wedge export threshold]
\label{thm:diffform-root-export-wedge-threshold}
At the threshold of \autoref{def:diffform-root-export-threshold-source}, the
exported wedge surface is exactly the visible tensor concatenation row, the
probe-append ledger, the degree-bookkeeping ledger, and the antisymmetry
ledgers over the carried input rows. The root threshold exports no exterior
law beyond these wedge rows.
\end{theorem}
\begin{proof}
Start from the wedge boundary of
\autoref{thm:diffform-root-wedge-ledger-obligation}. It says that an admitted
wedge row is exhausted by wedge ledger coverage, probe concatenation,
degree bookkeeping, and associator ledger rows over the displayed carrier and
classifier surface.

The tensor component is the visible $\TensorProductUp$ concatenation row
joining the tensor entries of the two carried forms. The probe component is
the displayed append of the two finite $\mathsf{ProbeBundle}$ spines, and the
degree component is the ledger recording the two input degrees and the output
degree row.

The antisymmetry contribution is not a hidden exterior identity. It is the
visible permutation and associator ledger attached to the carrier rows and
transported through $\hsame$. Since each wedge row cited by the root wedge
obligation refers back to those displayed histories, the threshold exports
exactly the stated wedge surface.
\end{proof}

\begin{theorem}[Differential-form downstream law separation]
\label{thm:diffform-root-export-downstream-law-separation}
The root threshold of \autoref{def:diffform-root-export-threshold-source}
separates the usable $\DiffFormUp$ surface from downstream exterior laws:
$\DeRhamUp$ must supply nilpotence, $\SymplecticUp$ must supply closedness and
nondegeneracy, and $\ContactUp$ must supply contact nonintegrability in their
own certificate surfaces. None of those laws is exported by the
$\DiffFormUp$ root threshold.
\end{theorem}
\begin{proof}
First apply
\autoref{thm:diffform-root-exterior-boundary-obligation}. It permits
exterior-derivative consumers to use only the displayed candidate ledger,
input row, degree shift, scalar transport, wedge-input stability, and
downstream scope rows.

Next apply \autoref{thm:diffform-downstream-consumer-boundary}. That theorem
identifies the rows consumed by $\DeRhamUp$, $\SymplecticUp$, and
$\ContactUp$, and states that $d^2=0$, closedness, nondegeneracy, and contact
nonintegrability must be supplied by the corresponding downstream chapters.

Combining the two boundary statements gives the separation. The root
threshold can export carried forms, classifier data, wedge ledgers, and
exterior-input rows, but it cannot certify an operator identity or geometric
law that is not one of those displayed rows.
\end{proof}

\begin{theorem}[Differential-form NameCert root threshold]
\label{thm:diffform-root-export-namecert-threshold}
The paper-side $\NameCert_{\DiffFormUp}$ root threshold is assembled by the
rows of \autoref{def:diffform-root-export-threshold-source}: the six-coordinate
carrier, the displayed classifier, the wedge ledger surface, the
exterior-derivative input boundary, and the downstream-consumer separation.
This assembly exports the usable $\DiffFormUp$ root surface and leaves
downstream operator and geometric laws off the root table.
\end{theorem}
\begin{proof}
Use \autoref{thm:diffform-root-source-obligation} for the source rows and
\autoref{thm:diffform-root-export-carrier-classifier-threshold} for the
carrier and classifier rows. These two statements bind the export surface to
the six displayed carrier coordinates and the classifier clauses already
available from the upstream manifold and tensor sources.

Use \autoref{thm:diffform-root-export-wedge-threshold} for the wedge surface.
It contributes exactly tensor concatenation, probe append, degree
bookkeeping, and antisymmetry ledger data over the carried forms.

Finally use \autoref{thm:diffform-root-export-downstream-law-separation}.
That statement imports the exterior-input boundary of
\autoref{thm:diffform-root-exterior-boundary-obligation} and the consumer
boundary of \autoref{thm:diffform-downstream-consumer-boundary}. The assembled
package is therefore a root threshold for $\NameCert_{\DiffFormUp}$ and not a
certificate for $d^2=0$, closedness, nondegeneracy, or contact
nonintegrability.
\end{proof}
