\chapter{A Concrete Naming Certificate for $\DyadicBisectionUp$}
\label{ch:concrete-instances-dyadicbisection-namecert}
\origin{human}

The $\DyadicBisectionUp$ interface names the finite bisection ledger used by real-and-completion consumers when an interval is refined by midpoint comparison. In the Bishop--Bridges constructive-analysis reading, bisection is a located finite interval process with explicit precision control; in the Moore interval-analysis reading, it is a finite enclosure refinement ledger. BEDC records the certificate rows themselves, not an analytic host search, a completed real intersection, or a hidden decision procedure.

The bisection carrier consumes the endpoint and dyadic-radius rows supplied by \autoref{ch:concrete-instances-rationalinterval-namecert}, \autoref{ch:concrete-instances-dyadicinterval-namecert}, and \autoref{ch:concrete-instances-dyadicratcore-namecert}. These rows provide the initial endpoint carrier, the midpoint and dyadic-radius tolerance ledger, and the finite comparison scale needed before the packet can expose nested-window data or hand off a $\RegSeqRatUp$, $\StreamNameUp$, or $\RealUp$ read.

\begin{definition}[DyadicBisection carrier]
\label{def:dyadic-bisection-carrier}
A $\DyadicBisectionUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
B=(I,\pi,M,L,J,E,R,S,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $I$ is the initial $\RationalIntervalUp$ row, including the endpoint order and endpoint readback rows used by downstream interval consumers;
\item $\pi$ is the unary precision row that names the requested finite stopping window;
\item $M$ is the finite chain of $\DyadicIntervalUp$ or $\DyadicMeshUp$ midpoint-comparison rows inspected during the run;
\item $L$ is the left/right branch ledger, with one displayed branch row for each midpoint comparison in $M$;
\item $J$ is the $\NestedIntervalUp$ refinement row obtained by threading the selected subintervals;
\item $E$ is the endpoint readback ledger for every retained lower endpoint, upper endpoint, midpoint, and displayed dyadic tolerance;
\item $R$ is the $\RegSeqRatUp$ handoff row extracted from the retained endpoint windows;
\item $S$ is the $\RealUp$ and $\StreamNameUp$ handoff surface through which real consumers read the same finite windows;
\item $H$ stores the $\hsame$ transports for the initial interval, precision row, midpoint rows, branch ledger, nested interval row, endpoint readbacks, and handoff rows;
\item $C$ stores the $\Cont$ routes for refinement, endpoint inspection, regular-sequence readback, and real-name consumption;
\item $P$ is the $\Pkg$ provenance row naming $\RationalIntervalUp$, $\DyadicIntervalUp$, $\DyadicMeshUp$, $\NestedIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\StreamNameUp$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\DyadicBisectionUp}$ registration row.
\end{enumerate}
The carrier exports only these finite rows. It has no coordinate for a host real root, a completed interval intersection, trichotomy on reals, Dedekind-cut data, or an ambient completeness proof.
\end{definition}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionTasteGate\_single\_carrier\_alignment}

\begin{definition}[DyadicBisection classifier]
\label{def:dyadic-bisection-classifier}
Two accepted $\DyadicBisectionUp$ carriers classify together when, after the displayed $\hsame$ and $\Cont$ transports, their initial interval rows, precision schedules, midpoint chains, branch ledgers, nested dyadic interval chains, endpoint readbacks, $\RegSeqRatUp$ rows, $\StreamNameUp$ windows, and $\RealUp$ handoff rows refine to the same finite observation window under the displayed dyadic tolerance.

Concretely, if the common stopping request is $n$, then each retained endpoint window is compared only after both packets are transported to the same finite tolerance row
$$
\varepsilon_n = 2^{-n}.
$$
Agreement means row-by-row equality of the transported branch choices and endpoint readbacks at that tolerance, followed by the inherited $\NestedIntervalUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ classifiers. No comparison is made by appealing to a host real value or to an infinite intersection.
\end{definition}

\begin{theorem}[DyadicBisection NameCert obligations]
\label{thm:dyadic-bisection-namecert-obligations}
The seed $\NameCert_{\DyadicBisectionUp}$ surface has five obligations:
\begin{enumerate}
\item carrier: formation of the finite $\mathsf{BHist}$ packet of \autoref{def:dyadic-bisection-carrier};
\item classifier: the finite-window classifier of \autoref{def:dyadic-bisection-classifier};
\item stability: componentwise preservation of the interval, precision, branch, nested-interval, endpoint, and handoff rows under displayed $\hsame$ transport and $\Cont$ refinement routes;
\item ledger exactness: every left/right branch choice is exactly the branch row attached to the corresponding midpoint comparison, and every retained endpoint read is one of the displayed dyadic ledger rows;
\item handoff: the retained endpoint windows are repacked into $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ rows without adding a host real intersection or an ambient completeness theorem.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_namecert\_obligations}
\begin{proof}
Carrier formation is the assembly of the displayed finite packet. Each coordinate is either a history row, a transport row, a continuation route, package provenance, or a local naming row owned by the listed dependency certificates.

The classifier is finite because the stopping request fixes the displayed tolerance and the inspected midpoint chain. After transporting both carriers to that window, comparison is componentwise on the initial interval, precision schedule, branch ledger, nested interval row, endpoint readbacks, and handoff rows.

Stability follows the same component order. Transport first moves the initial interval and precision rows, then the midpoint rows and branch choices, then the nested interval and endpoint ledgers, and finally the regular-sequence, stream, and real-name handoff rows.

Ledger exactness is the branch-row invariant: the $k$th branch coordinate is the only source of the $k$th left/right choice, and the retained endpoint rows are precisely the rows routed by $C$ and transported by $H$.

The handoff obligation repacks the finite retained windows into $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ surfaces. Since the carrier contains no host real, infinite intersection, or completeness coordinate, no such object can be exported.
\end{proof}

\begin{theorem}[DyadicBisection nested interval bridge]
\label{thm:dyadic-bisection-nested-interval-bridge}
For every accepted $\DyadicBisectionUp$ carrier $B$, the displayed branch ledger determines a finite $\NestedIntervalUp$ refinement row whose $k$th interval is the subinterval selected by the $k$th midpoint comparison. The bridge exposes the initial $\RationalIntervalUp$ row, the dyadic midpoint ledger, the left/right branch ledger, the endpoint readbacks, and the $\NestedIntervalUp$ row, and it exports no completed intersection of the nested intervals.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_nested\_interval\_bridge}
\begin{proof}
Project the carrier of \autoref{def:dyadic-bisection-carrier}. The midpoint chain $M$ and branch ledger $L$ have the same finite length, so the $k$th midpoint comparison has a unique displayed branch row.

Thread the interval row forward along these branch choices. At each step, the retained lower endpoint, upper endpoint, midpoint, and tolerance rows are already present in the endpoint ledger $E$, and the transport rows in $H$ record that the selected subinterval is the continuation of the previous interval.

Pack the resulting finite chain into the $\NestedIntervalUp$ row $J$. This row is the bridge available to downstream consumers: it records the nested finite refinement path but does not claim that the infinite intersection exists as a host real object.
\end{proof}

\begin{theorem}[DyadicBisection real stream handoff]
\label{thm:dyadic-bisection-real-stream-handoff}
For every accepted $\DyadicBisectionUp$ carrier and every unary precision request $n$, the consumer-visible $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ reads factor through the retained dyadic endpoint window at tolerance $2^{-n}$, the branch ledger prefix needed to reach that window, the $\NestedIntervalUp$ refinement row, the displayed $\hsame$ transports, the $\Cont$ routes, the $\Pkg$ provenance row, and the local $\NameCert$ row.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_real\_stream\_endpoint\_scope}
\begin{proof}
Start with the precision row $\pi$ and the displayed request $n$. The carrier uses that row to select a finite branch-prefix length and the corresponding retained endpoint window in $E$.

Use \autoref{thm:dyadic-bisection-nested-interval-bridge} to route the selected endpoint window through the nested interval row. The branch prefix identifies the retained subinterval, while the endpoint ledger supplies the rational lower and upper reads at the requested tolerance.

The $\RegSeqRatUp$ row $R$ consumes those retained rational windows. The $\StreamNameUp$ and $\RealUp$ rows in $S$ then expose the same finite observation to real consumers through the displayed transports, continuation routes, package provenance, and local certificate row.

Thus every real-facing read has the stated finite factorization. The handoff does not use root existence, real trichotomy, Dedekind cuts, host real equality, or a host intersection theorem.
\end{proof}

\begin{theorem}[DyadicBisection nested window handoff]
\label{thm:dyadic-bisection-nested-window-handoff}
For every accepted $\DyadicBisectionUp$ carrier and every unary precision request $n$, the $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ reads are determined by the unique branch-prefix ledger segment that reaches the retained nested interval window at tolerance $2^{-n}$, together with the endpoint readbacks and displayed $\hsame$ and $\Cont$ transports. This handoff introduces no host intersection, completed real root, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_nested\_window\_handoff}
\begin{proof}
Project the branch ledger of \autoref{def:dyadic-bisection-carrier}. The precision request $n$ selects the finite prefix length whose branch choices reach the retained endpoint window recorded in $E$.

Apply \autoref{thm:dyadic-bisection-nested-interval-bridge}. The selected branch prefix determines the corresponding $\NestedIntervalUp$ row, and that row exposes the retained lower endpoint, upper endpoint, midpoint, and tolerance readbacks from the finite ledger.

Now apply \autoref{thm:dyadic-bisection-real-stream-handoff}. The $\RegSeqRatUp$ row reads those retained rational windows, while the $\StreamNameUp$ and $\RealUp$ rows expose the same finite observation through the displayed transports and continuation routes.

The carrier has no field for an intersection of all retained intervals and no field for a completeness theorem. Therefore the nested window is the exact surface consumed by the handoff.
\end{proof}

\begin{theorem}[DyadicBisection branch endpoint determinacy]
\label{thm:dyadic-bisection-branch-endpoint-determinacy}
For every accepted $\DyadicBisectionUp$ carrier and every unary precision
request $n$, the finite branch-prefix ledger segment that reaches the retained
window at tolerance $2^{-n}$ uniquely determines the retained lower endpoint,
retained upper endpoint, midpoint, tolerance row, nested interval row, and the
downstream $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ handoff rows. No host
root, infinite intersection, trichotomy, or completeness row participates in
this determination.
\end{theorem}
\begin{proof}
Project the accepted carrier of \autoref{def:dyadic-bisection-carrier}. The
unary request $n$ selects a finite prefix of the branch ledger, and each row of
that prefix chooses one retained dyadic subinterval from the previous endpoint
window.

Apply the nested interval bridge of
\autoref{thm:dyadic-bisection-nested-interval-bridge}. The selected branch
prefix fixes the retained lower endpoint, upper endpoint, midpoint, and
tolerance readback in the endpoint ledger, then packs the same finite chain
into the $\NestedIntervalUp$ row.

Next use the real stream handoff of
\autoref{thm:dyadic-bisection-real-stream-handoff} and the nested window
handoff of \autoref{thm:dyadic-bisection-nested-window-handoff}. The
$\RegSeqRatUp$ row consumes the retained endpoint windows, and the
$\StreamNameUp$ and $\RealUp$ rows expose that same finite observation through
the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The construction has used only the finite carrier rows, the nested interval
bridge, and the handoff routes. Since none of these rows contains a host root,
an infinite intersection, a trichotomy decision, or a completeness principle,
the branch-prefix ledger segment is the determinant of the retained endpoint
window and its downstream reads.
\end{proof}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_branch\_endpoint\_transport}

\begin{theorem}[DyadicBisection branch nested-window scope]
\label{thm:dyadic-bisection-branch-nested-window-scope}
For every accepted $\DyadicBisectionUp$ carrier over $\DyadicIntervalUp$, $\DyadicMeshUp$, $\NestedIntervalUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$, the selected branch ledger determines the finite nested-window row and transports it through the displayed $\hsame$ and $\Cont$ rows to the same $\RealUp$ seal endpoint. The scope is the carried packet
$$
B=(I,\pi,M,L,J,E,R,S,H,C,P,N),
$$
where the finite branch prefix in $L$ determines the retained endpoint rows in $E$, the nested interval row $J$, the regular readback $R$, and the real-stream handoff surface $S$.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_branch\_nested\_window\_scope}
\begin{proof}
Start with the branch ledger and its endpoint determination. Apply \autoref{thm:dyadic-bisection-branch-endpoint-determinacy}: for a unary precision request, the finite branch prefix fixes the retained endpoint window, tolerance row, nested interval row, and downstream handoff rows.

Next identify the nested-window row. Apply \autoref{thm:dyadic-bisection-nested-interval-bridge} to thread the branch choices through the dyadic midpoint chain and pack the retained subintervals into $J$.

Now use \autoref{thm:dyadic-bisection-nested-window-handoff}. The same branch prefix and endpoint readbacks determine the $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ reads through the displayed transport and continuation rows.

Finally apply \autoref{thm:dyadic-bisection-real-stream-handoff} to bind the resulting regular and stream reads to the real-facing handoff surface $S$. The construction never leaves the displayed carrier rows, so it exports no host root, infinite intersection, trichotomy decision, or ambient completeness row.
\end{proof}

\begin{theorem}[DyadicBisection selector interval stability]
\label{thm:dyadic-bisection-selector-interval-stability}
For an accepted $\DyadicBisectionUp$ carrier
$$
B=(I,\pi,M,L,J,E,R,S,H,C,P,N),
$$
transporting the initial interval $I$, precision row $\pi$, midpoint chain $M$, and branch ledger $L$ through the displayed $\hsame$ ledger $H$ and $\Cont$ routes $C$ preserves the selected retained interval row. It also preserves the retained endpoint readbacks in $E$, the $\NestedIntervalUp$ row $J$, and the downstream $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ handoff rows $R,S$.

The stability statement is entirely internal to the displayed bisection carrier, package provenance $P$, and local $\NameCert_{\DyadicBisectionUp}$ row $N$; it does not rely on a hidden root, trichotomy, or a completed interval intersection.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_nonempty\_iff}
\begin{proof}
First apply \autoref{thm:dyadic-bisection-nested-interval-bridge}. The transported branch ledger threads the transported midpoint chain into the same finite $\NestedIntervalUp$ row, so the selected retained interval row remains a displayed row of the carrier.

Next use \autoref{thm:dyadic-bisection-branch-endpoint-determinacy}. Once the retained interval row is fixed at the requested precision, the lower endpoint, upper endpoint, midpoint, tolerance row, and downstream handoff rows are determined by the same finite branch-prefix ledger.

Apply \autoref{thm:dyadic-bisection-nested-window-handoff} to identify the $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ reads with that retained nested window and its endpoint readbacks. The transports in $H$ and routes in $C$ move these rows componentwise.

Finally use \autoref{thm:dyadic-bisection-branch-nested-window-scope}. The selected branch ledger, nested row, endpoint ledger, and handoff rows remain inside the carried packet $B$, so no host root, real trichotomy, or completed intersection object participates in the stability claim.
\end{proof}

\begin{theorem}[DyadicBisection public branch totality]
\label{thm:dyadic-bisection-public-branch-totality}
For every accepted $\DyadicBisectionUp$ carrier
$$
B=(I,\pi,M,L,J,E,R,S,H,C,P,N),
$$
and every unary precision request $n$, the public finite branch-consumer route
is exhausted by the branch endpoint transport, the branch nested-window scope,
the real stream endpoint scope, and the retained interval nonempty read. The
route exposes exactly the initial interval row, precision row, finite midpoint
chain, selected branch-prefix ledger, retained endpoint readbacks,
$\NestedIntervalUp$ row, $\RegSeqRatUp$ row, $\StreamNameUp$ window, $\RealUp$
handoff surface, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$ provenance,
and $\NameCert_{\DyadicBisectionUp}$ row.

It exports no host root, infinite intersection, trichotomy decision, Dedekind
cut, hidden midpoint oracle, or ambient completeness row.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_public\_branch\_totality}
\begin{proof}
Begin with the selected branch-prefix ledger for the request $n$. Apply
\autoref{thm:dyadic-bisection-branch-endpoint-determinacy} to determine the
retained lower endpoint, upper endpoint, midpoint, tolerance row, nested
interval row, and downstream handoff rows.

Next apply \autoref{thm:dyadic-bisection-branch-nested-window-scope}. This
places the branch prefix, endpoint rows, nested row, regular readback, and
real-stream handoff inside the displayed carrier packet and transports them
through $H$ and $C$.

Use \autoref{thm:dyadic-bisection-real-stream-handoff} to expose the
$\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ consumer reads at the same
finite retained endpoint window.

Finally apply the retained interval stability theorem of this chapter. The
retained interval row and its endpoint readbacks remain componentwise stable
under the displayed transports and continuation routes. Hence the public route
is exactly the finite packet listed above, with no off-table analytic object.
\end{proof}

\begin{theorem}[DyadicBisection retained interval consumer route]
\label{thm:dyadic-bisection-retained-interval-consumer-route}
Two accepted $\DyadicBisectionUp$ carriers with the same transported initial
interval, precision row, midpoint chain, branch ledger, retained endpoint
readbacks, nested interval row, $\RegSeqRatUp$ row, $\StreamNameUp$ window,
$\RealUp$ handoff surface, $\hsame$ transports, $\Cont$ routes, $\mathsf{Pkg}$
provenance, and $\NameCert_{\DyadicBisectionUp}$ row have the same public
retained-interval consumer route. Conversely, equality of the public
retained-interval route is witnessed by componentwise agreement of those
displayed finite rows.

The route is the public object surface for dyadic bisection consumers. It does
not assert a completed intersection, a host real root, real trichotomy, or a
Dedekind-cut carrier.
\end{theorem}
\begin{proof}
For the forward direction, assume componentwise agreement of the displayed
finite rows. Apply
\autoref{thm:dyadic-bisection-public-branch-totality} to both carriers. Each
public branch-consumer route is exhausted by the same finite branch prefix,
endpoint ledger, nested interval row, regular readback, stream window, real
handoff, transport, continuation, package, and certificate rows.

The retained interval stability theorem identifies the retained interval row
and endpoint readbacks after transport. The branch nested-window scope and real
stream handoff then route the same retained window to the same public consumer
surface.

For the reverse direction, suppose the public retained-interval consumer routes
are equal. Project the route through
\autoref{thm:dyadic-bisection-public-branch-totality}. The projection exposes
only the listed finite carrier rows, so route equality supplies componentwise
agreement of the interval, precision, midpoint, branch, endpoint, nested,
regular, stream, real, transport, continuation, package, and certificate rows.

No further coordinate is available in the carrier. Thus equality of the public
route is exactly componentwise agreement of the displayed finite rows, and the
off-table host and completeness objects cannot participate.
\end{proof}
\leanchecked{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_consumer\_route}

\begin{theorem}[DyadicBisection StreamName retained route]
\label{thm:dyadic-bisection-streamname-retained-route}
Any retained-interval consumer of an accepted $\DyadicBisectionUp$ carrier that hands off to $\StreamNameUp$ must read the rational interval row, dyadic interval row, $\DyadicRatCoreUp$ radius row, retained branch endpoint row, nested window row, displayed $\hsame$ transport, displayed $\Cont$ route, $\Pkg$ provenance, and local $\NameCert_{\DyadicBisectionUp}$ row before any $\RegSeqRatUp$ or $\RealUp$ read. The retained StreamName route exposes the finite bisection packet, not a host root, completed intersection, real trichotomy, or Dedekind-cut carrier.
\end{theorem}
\begin{proof}
First use the nested interval bridge. It turns the midpoint chain and retained branch choices into the finite nested interval row and retained endpoint readbacks.

Next apply the real stream handoff and nested-window handoff. They route the retained endpoint data through the $\StreamNameUp$ window and then toward the $\RegSeqRatUp$ and $\RealUp$ reads without leaving the displayed transport and continuation rows.

Finally apply the retained interval consumer route. It identifies the public retained route with the rational interval, dyadic interval, radius, retained endpoint, nested window, transport, continuation, package, and certificate rows, so no completion-level or host-level object is exposed before the finite StreamName route has been read.
\end{proof}

\closureat{DyadicBisectionUp}{seedStr}
\closureat{DyadicBisectionUp}{obligationStr}
\closureat{DyadicBisectionUp}{scopedStr}
\closureat{DyadicBisectionUp}{publicStr}[BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_nonempty\_iff]
\closureat{DyadicBisectionUp}{bridgedStr}[BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_nonempty\_iff]
\closureat{DyadicBisectionUp}{matureStr}[BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_nonempty\_iff]

\begin{closurestatus}{\DyadicBisectionUp}
  \constructivestory{A $\DyadicBisectionUp$ packet is generated from an initial $\RationalIntervalUp$ row, a unary precision row, finite $\DyadicIntervalUp$ or $\DyadicMeshUp$ midpoint comparisons, an exact left/right branch ledger, a $\NestedIntervalUp$ refinement row, endpoint readbacks, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$ handoff rows, displayed $\hsame$ and $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The public packet binds the carrier, finite-window classifier, NameCert obligation surface, nested interval bridge, real-stream handoff, branch endpoint determinacy, branch nested-window scope, selector interval stability, public branch totality, and retained-interval consumer route for dyadic bisection over $\RationalIntervalUp$, $\DyadicIntervalUp$, $\DyadicMeshUp$, $\NestedIntervalUp$, $\RegSeqRatUp$, $\StreamNameUp$, and $\RealUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.DyadicBisectionUp.DyadicBisectionCarrier\_retained\_interval\_nonempty\_iff}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close completeness, root existence, trichotomy, Dedekind cuts, uniqueness of a limit point, or host real intersection.}
  \upgradepath{No further paper-theory upgrade remains; Lean bridge checking remains a separate verification-axis task.}
\end{closurestatus}
