\chapter{A Concrete Naming Certificate for $\ContactUp$}
\label{ch:concrete-instances-contact-namecert}
\origin{human}

The contact-structure interface $\ContactUp$ packages a maximally nonintegrable hyperplane field on an odd-dimensional manifold carrier, recorded as a $1$-form whose top-degree wedge is nondegenerate. It depends on $\NameCert_{\DiffFormUp}$ (\autoref{ch:concrete-instances-diffform-namecert}) and $\NameCert_{\ManifoldUp}$ (\autoref{ch:concrete-instances-manifold-namecert}).

\section{Carrier definition}
\label{sec:contact-carrier}

\begin{definition}[ContactUp carrier-classifier surface]
\label{def:contactup-carrier-classifier-surface}
Fix a $\NameCert_{\ManifoldUp}$ source $M$ and a $\NameCert_{\DiffFormUp}$ source $\Omega$. A $\ContactUp$ carrier-classifier surface over $BHist$ is the displayed BEDC package
$$
\mathsf{ContactCarrierClassifier}_{M,\Omega}.
$$
Its source rows are the $BHist$ carrier rows inherited from $M$ and $\Omega$, the odd-dimensional manifold witness on the shared manifold endpoint, a carried $\DiffFormUp$ degree-one form row $\alpha$, a contact hyperplane row $\ker(\alpha)$ on the same manifold carrier, an exterior-derivative input row $d\alpha$, the wedge ladder rows for $\alpha\wedge(d\alpha)^k$, and the top wedge row $\alpha\wedge(d\alpha)^n$ when the displayed dimension row is $2n+1$.

Its classifier is the restriction of $\hsame$ to rows that preserve the shared $\ManifoldUp$ carrier, the $\DiffFormUp$ one-form row, the hyperplane row, the exterior-derivative input row, and every displayed wedge-ladder row. The surface contains no nonintegrability primitive and no standard bridge row.
\end{definition}
\leandef{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface}
\leanchecked{BEDC.Derived.ContactUp.ContactTasteGate\_single\_carrier\_alignment}

\begin{theorem}[ContactUp form-row obligation surface]
\label{thm:contactup-form-row-obligation}
Every $\ContactUp$ carrier-classifier surface of \autoref{def:contactup-carrier-classifier-surface} exposes exactly the $\ManifoldUp$ source, the $\DiffFormUp$ contact consumer face, the degree-one form row $\alpha$, the exterior-derivative input row $d\alpha$, and the wedge ladder rows $\alpha\wedge(d\alpha)^k$ routed by the $\DiffFormUp$ root threshold. It exposes no nilpotence row, no symplectic closedness row, no contact nonintegrability witness, and no standard bridge as part of the $\DiffFormUp$ root face.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_form\_row\_obligation}
\begin{proof}
Unpack \autoref{def:contactup-carrier-classifier-surface}. The source fields are the shared $\ManifoldUp$ carrier and the $\DiffFormUp$ carried rows for the one-form, exterior-input, and wedge ladder.

Apply \autoref{thm:diffform-root-consumer-face-coverage} and \autoref{thm:diffform-root-consumer-face-disjointness}. They place the contact reads in the $\ContactUp$ consumer face and separate them from the de Rham, symplectic, and shared root laws.

Finally apply \autoref{thm:diffform-root-export-wedge-threshold}. The threshold exports carried forms, classifier data, wedge ledgers, and exterior-input routing, so the $\ContactUp$ surface receives exactly the form row, derivative input row, and wedge ladder rows stated above.
\end{proof}

\section{The certificate}
\label{sec:contact-certificate}

\begin{theorem}[ContactUp nondegeneracy obligation]
\label{thm:contactup-nondegeneracy-obligation}
For a $\ContactUp$ carrier-classifier surface over a displayed dimension row $2n+1$, top-degree wedge nondegeneracy is a $\ContactUp$-local obligation transported by the $\ContactUp$ classifier:
$$
\mathsf{Nondegenerate}_{M}(\alpha\wedge(d\alpha)^n).
$$
The $\DiffFormUp$ root supplies the carried form row, exterior-derivative input row, and wedge routing needed to form the top row, but it does not supply this nondegeneracy predicate as a primitive.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_top\_wedge\_transport}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_nondegeneracy\_obligation}
\begin{proof}
Begin with the top wedge row named in \autoref{def:contactup-carrier-classifier-surface}. It is assembled from the degree-one row, the exterior-derivative input row, and the wedge ladder exported by \autoref{thm:diffform-root-export-wedge-threshold}.

Now use the classifier clause of the same definition. It transports the shared manifold carrier, the one-form row, the derivative input row, and the wedge ladder rows, so the nondegeneracy predicate is stated on the transported $\ContactUp$ surface.

The exclusion clause follows from \autoref{thm:diffform-root-consumer-face-disjointness}: $\DiffFormUp$ exports routing rows to the contact consumer face, while contact nonintegrability remains outside the shared root primitive surface.
\end{proof}
\leanvariant{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_nondegeneracy\_obligation}

\begin{theorem}[ContactUp ledger exactness obligation]
\label{thm:contactup-ledger-exactness-obligation}
The $\ContactUp$ ledger and exactness obligation records exactly the hidden manifold chart rows supplied by the $\ManifoldUp$ source, the one-form source row $\alpha$, the exterior-derivative input row $d\alpha$, the wedge ladder rows $\alpha\wedge(d\alpha)^k$, the top wedge row $\alpha\wedge(d\alpha)^n$, the nonintegrability witness of \autoref{thm:contactup-nondegeneracy-obligation}, and a coverage, soundness, and completeness predicate for the carrier-classifier surface of \autoref{def:contactup-carrier-classifier-surface}.

The obligation is exact only when every certified contact read factors through that carrier-classifier surface and every listed ledger row is classified by the restricted $\hsame$ transport named there.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactUpLedgerExactness\_obligation}
\begin{proof}
Unpack \autoref{def:contactup-carrier-classifier-surface}. Its source and classifier clauses list the $\ManifoldUp$ chart carrier, the $\DiffFormUp$ one-form row, the exterior-input row, the wedge ladder, the top wedge row, and the hyperplane row.

Apply \autoref{thm:contactup-form-row-obligation} to identify the contact consumer face and the routed form rows, then apply \autoref{thm:contactup-nondegeneracy-obligation} for the local nonintegrability witness.

The coverage predicate says every certified contact read lands in this displayed package. Soundness says each such read is one of the listed rows. Completeness says each listed row is available to the carrier-classifier. These three clauses are precisely the ledger exactness obligation.
\end{proof}

\begin{theorem}[ContactUp public NameCert export]
\label{thm:contactup-public-namecert-export}
The carrier-classifier surface of
\autoref{def:contactup-carrier-classifier-surface}, the form-row obligation of
\autoref{thm:contactup-form-row-obligation}, the nondegeneracy obligation of
\autoref{thm:contactup-nondegeneracy-obligation}, and the ledger exactness
obligation of \autoref{thm:contactup-ledger-exactness-obligation} assemble the
public $\NameCert_{\ContactUp}$ surface over $\mathsf{BHist}$, the
$\ManifoldUp$ carrier, the $\DiffFormUp$ one-form row, the exterior-input row,
the wedge ladder, the top wedge, the restricted $\hsame$ classifier, and the
exact ledger.

This public surface exports the carried contact rows and their exact ledger. It
does not export a separate nonintegrability primitive and does not include a
standard bridge.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_public\_namecert\_export}
\begin{proof}
Project the carrier field from
\autoref{def:contactup-carrier-classifier-surface}. The carrier consists of
the shared $\ManifoldUp$ endpoint, the $\DiffFormUp$ degree-one form row, the
exterior-input row, the wedge ladder, and the top wedge row over
$\mathsf{BHist}$.

Project the classifier field from the same definition. It is the restriction
of $\hsame$ to transports preserving the manifold carrier, one-form row,
hyperplane row, exterior-input row, and wedge-ladder rows.

Project the routed form face from
\autoref{thm:contactup-form-row-obligation} and the local top-wedge condition
from \autoref{thm:contactup-nondegeneracy-obligation}. These two rows provide
the form and nondegeneracy fields without adding a nonintegrability primitive.

Finally repack the coverage, soundness, completeness, and row list of
\autoref{thm:contactup-ledger-exactness-obligation} as the exact ledger field.
Because every projected row is already part of the displayed
carrier-classifier surface, the public certificate contains no standard bridge
row.
\end{proof}

\begin{definition}[ContactUp standard bridge surface]
\label{def:contact-standard-bridge-surface}
The $\ContactUp$ standard bridge surface is the public $\ContactUp$
carrier-classifier rows, the form-row obligation, the nondegeneracy row, the
ledger exactness row, and the public $\NameCert$ export, read as the source
side of the standard contact-structure interpretation. Its source side is
exactly the surface displayed by
\autoref{thm:contactup-public-namecert-export}.
\end{definition}
\leandef{BEDC.Derived.ContactUp.ContactStandardBridgeSurface}

\begin{theorem}[ContactUp public bridge compatibility]
\label{thm:contact-public-bridge-compatibility}
Every row interpreted by the bridge surface of
\autoref{def:contact-standard-bridge-surface} is already one of the public
$\ContactUp$ rows, and every public $\ContactUp$ row has a corresponding
bridge-side row. The bridge adds no host manifold, no open-cover compactness
condition, and no external equality beyond the public carrier, classifier,
obligation, ledger, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactStandardBridgeSurface\_public\_bridge\_compatibility}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_public\_bridge\_compatibility}
\begin{proof}
Use \autoref{thm:contactup-form-row-obligation} for the routed one-form,
exterior-input, and wedge-ladder rows, then
\autoref{thm:contactup-nondegeneracy-obligation} for the contact-local
top-wedge row.

Apply \autoref{thm:contactup-ledger-exactness-obligation}. Its coverage,
soundness, and completeness clauses say that the listed bridge reads are
exactly the certified public contact reads.

Finally use \autoref{thm:contactup-public-namecert-export}. It repacks those
rows as the public $\NameCert_{\ContactUp}$ surface, so the correspondence is
row-for-row and introduces no host manifold, compactness, or external equality
datum.
\end{proof}

\begin{theorem}[ContactUp mature consumer completeness]
\label{thm:contactup-mature-consumer-completeness}
Every $\ContactUp$ consumer of the public bridge reads exactly the
$\ManifoldUp$ carrier, the $\DiffFormUp$ one-form row, the exterior-input row,
the wedge ladder rows, the top-wedge nondegeneracy row, the exact ledger, and
the public bridge compatibility rows already named by
\autoref{thm:contactup-public-namecert-export} and
\autoref{thm:contact-public-bridge-compatibility}. No extra host manifold,
compactness condition, or equality source is exported.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactStandardBridgeSurface\_mature\_consumer\_completeness}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_mature\_consumer\_completeness}
\begin{proof}
First apply \autoref{thm:contactup-form-row-obligation}. It identifies the
contact consumer face with the routed $\DiffFormUp$ one-form, exterior-input,
and wedge rows over the shared $\ManifoldUp$ carrier.

Next apply \autoref{thm:contactup-nondegeneracy-obligation} and
\autoref{thm:contactup-ledger-exactness-obligation}. These supply the local
top-wedge nondegeneracy row and the exact coverage, soundness, and completeness
ledger for the displayed carrier-classifier surface.

Finally use \autoref{thm:contactup-public-namecert-export} to repack those rows
as the public $\NameCert_{\ContactUp}$ surface, and use
\autoref{thm:contact-public-bridge-compatibility} to compare the public surface
with the bridge surface. The compatibility theorem states that the bridge adds
no host manifold, compactness, or external equality datum, so the listed rows
are the complete consumer boundary.
\end{proof}

\closureat{ContactUp}{matureStr}

\begin{closurestatus}{\ContactUp}
  \constructivestory{A contact surface is built over a shared $\ManifoldUp$ and $\DiffFormUp$ source by displaying an odd-dimensional manifold row, a carried degree-one form $\alpha$, its hyperplane row, an exterior-derivative input $d\alpha$, the wedge ladder $\alpha\wedge(d\alpha)^k$, and the top-degree wedge row. A history enters the carrier only through those routed form rows, and two accepted surfaces classify together when $\hsame$ preserves the shared manifold endpoint, the one-form, the hyperplane row, the exterior-input row, and every wedge-ladder row. The source covers exactly the manifold plus routed one-form data, the pattern records the top wedge nondegeneracy condition on dimension $2n+1$, and the ledger keeps chart rows, the one-form source, derivative input, wedge ladder, top wedge, and local nonintegrability witness aligned. The public certificate obligations are therefore the displayed carrier row, restricted classifier reflexivity, symmetry, transitivity, and closure of all listed form rows under that classifier, with coverage, soundness, and completeness supplied by the exact ledger. A history $h$ lies in the signature gap of a $\ContactUp$ token $p$ when the source accepts such a form surface for $h$, the signature relation pairs it with an answer surface and evidence ledger, and token introduction identifies that answer as $p$; unfolded, $h$ carries the same odd-dimensional endpoint, one-form, derivative input, wedge ladder, and nondegenerate top wedge encoded by $p$. The surface deliberately reads the nonintegrability condition as this top-wedge row rather than as a separate primitive, and it exports no standard bridge. The chapter registers this routed one-form construction under the name $\ContactUp$; no closed carrier implementation, host contact manifold, or independent nonintegrability theorem is assumed.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The public boundary is exactly the carrier-classifier surface, form-row obligation, nondegeneracy obligation, and exact ledger assembled in \autoref{thm:contactup-public-namecert-export}.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim a closed ContactUp carrier implementation, a proved nonintegrability theorem, Lean bridge verification, or mature examples.}
  \upgradepath{The paper-side theory axis is complete; Lean bridge verification remains a separate verification-axis obligation.}
\end{closurestatus}

\begin{definition}[ContactUp coannihilating integrability row]
\label{def:contactup-coannihilating-integrability-row}
Let $C$ be a $\ContactUp$ carrier-classifier surface of \autoref{def:contactup-carrier-classifier-surface} over a displayed dimension row $2n+1$ with $n\ge1$. Write its shared manifold carrier as $M$, its carried one-form row as $\alpha$, its hyperplane row as $\ker(\alpha)$, its exterior-input row as $d\alpha$, and its wedge ladder as $\alpha\wedge(d\alpha)^k$.

A displayed row $I_{\mathcal{D}}$ is a $\ContactUp$ coannihilating integrability row on $C$ when its contact-relevant fields are all on the same $\ManifoldUp$ carrier $M$ and consist of the following data:
\begin{itemize}
  \item a hyperplane-distribution row $\mathcal{D}$ classified with the displayed contact hyperplane row $\ker(\alpha)$;
  \item an annihilator-identification row $\mathsf{Ann}(\mathcal{D})\sim\alpha$;
  \item a codimension-one Frobenius row for that annihilator, transported along $\mathsf{Ann}(\mathcal{D})\sim\alpha$;
  \item the resulting Frobenius wedge-collapse ledger along the displayed $\ContactUp$ wedge ladder:
  $$
  \forall k\ (1\le k\le n\Rightarrow \alpha\wedge(d\alpha)^k\sim0).
  $$
\end{itemize}
The row is admitted only when these fields are transported by the restricted $\ContactUp$ classifier, so the manifold carrier, one-form row, hyperplane row, exterior-input row, and wedge-ladder rows are the same rows read by $C$.
\end{definition}
\leanchecked{BEDC.Derived.ContactUp.ContactCoannihilatingIntegrabilityRow\_transport\_with\_empty}

\begin{theorem}[Contact top wedge excludes coannihilating integrability]
\label{thm:contact-top-wedge-excludes-coannihilating-integrability}
Let $C$ be a $\ContactUp$ carrier-classifier surface of \autoref{def:contactup-carrier-classifier-surface} over a displayed dimension row $2n+1$ with $n\ge1$. Suppose $C$ carries the top-wedge nondegeneracy row
$$
\alpha\wedge(d\alpha)^n\not\sim0.
$$
Then no $\ContactUp$ coannihilating integrability row $I_{\mathcal{D}}$ of \autoref{def:contactup-coannihilating-integrability-row} is admitted on the same carrier. Equivalently, no displayed integrable-distribution row $\mathcal{D}$ on the same $\ManifoldUp$ carrier whose annihilator is classified with $\alpha$ can coexist with the displayed $\ContactUp$ top-wedge row.
\end{theorem}
\leanchecked{BEDC.Derived.ContactUp.ContactCarrierClassifierSurface\_top\_wedge\_excludes\_coannihilating\_integrability}
\begin{proof}
Assume that such a row $I_{\mathcal{D}}$ is admitted. By \autoref{def:contactup-coannihilating-integrability-row}, the distribution row lies on the same $\ManifoldUp$ carrier as $C$, its hyperplane row is classified with $\ker(\alpha)$, and its annihilator row is classified with $\alpha$.

The Frobenius part of the admitted row is therefore read on the same carried one-form row and the same exterior-input row $d\alpha$. Since $n\ge1$, the Frobenius wedge-collapse ledger in \autoref{def:contactup-coannihilating-integrability-row} applies to the displayed ladder index $k=n$ and gives
$$
\alpha\wedge(d\alpha)^n\sim0.
$$

It remains to check that this is the same top-wedge endpoint as the contact nondegeneracy row. The carrier definition \autoref{def:contactup-carrier-classifier-surface} includes the one-form row, hyperplane row, exterior-input row, every wedge-ladder row, and the top wedge row on one shared manifold endpoint. The form-row obligation \autoref{thm:contactup-form-row-obligation} routes these rows through the $\ContactUp$ consumer face, and \autoref{thm:contactup-nondegeneracy-obligation} places the nondegeneracy predicate on that transported top wedge. Thus the zero endpoint obtained from $I_{\mathcal{D}}$ and the nondegenerate endpoint carried by $C$ address the same row $\alpha\wedge(d\alpha)^n$.

The displayed nondegeneracy hypothesis says that this row is not classified with zero, while the Frobenius wedge-collapse ledger says that it is classified with zero. An admitted row cannot satisfy both predicates on the same classified endpoint. Hence the assumed $I_{\mathcal{D}}$ is not admitted.
\end{proof}
