\chapter{A Concrete Naming Certificate for $\StationaryRationalDiagonalUp$}
\label{ch:concrete-instances-stationaryrationaldiagonal-namecert}
\origin{human}

The $\StationaryRationalDiagonalUp$ interface names the finite packet obtained
from a stationary rational regular Cauchy input and its diagonal representative.
It sits at the Real and Completion boundary: the source is a $\RatUp$ row read
as a constant $\StreamNameUp$ and $\RegSeqRatUp$ object, while the consumer sees
only the associated $\RealUp$ seal surface. The packet carries no quotient of
regular streams, host real equality, ambient completeness principle, or hidden
limit selection.

The packet consumes substantive source rows from the rational seed surface of
\autoref{ch:concrete-instances-rat-namecert}, the constant-window carrier of
\autoref{ch:concrete-instances-streamname-namecert}, the regular rational
readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the seal
boundary of \autoref{ch:concrete-instances-real-namecert}; these are the
displayed inputs to the diagonal packet, not decorative references.

The stationary diagonal is the degenerate tail-selection case recorded by
\autoref{ch:concrete-instances-regularcauchytailselector-namecert}: every
requested selector window is constant at the displayed $\RatUp$ seed, and the
$\RealUp$ seal handoff therefore consumes the same selected-tail discipline
through a singleton constant window.

\begin{definition}[Stationary rational diagonal carrier]
\label{def:stationary-rational-diagonal-carrier}
A $\StationaryRationalDiagonalUp$ carrier is a finite $\mathsf{BHist}$ row
$$
S=(q,C,R,D,E,H,K,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $q$ is the $\RatUp$ source row;
\item $C$ is the constant $\StreamNameUp$ schedule generated by $q$;
\item $R$ is the stationary $\RegSeqRatUp$ readback row whose inspected windows
all return $q$;
\item $D$ is the diagonal selector row that always selects the stationary
member and the requested regular-sequence window;
\item $E$ is the $\RealUp$ seal ledger for the constant rational embedding;
\item $H$ records the displayed $\hsame$ transports for the rational source,
stream schedule, regular readback, diagonal selector, and real seal;
\item $K$ records the visible $\Cont$ routes by which consumers reach the
selected constant windows;
\item $P$ is the $\Pkg$ provenance naming the $\RatUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and
$\NameCert$ dependency rows;
\item $N$ is the local $\NameCert_{\StationaryRationalDiagonalUp}$ provenance
row.
\end{enumerate}
The classifier compares accepted carriers only by the displayed $\RatUp$ seed
classifier, the constant $\StreamNameUp$ readback, the stationary
$\RegSeqRatUp$ window row, and the $\RealUp$ seal-facing route, transported
through the listed $\hsame$ and $\Cont$ rows.
\end{definition}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Stationary rational diagonal NameCert obligation surface]
\label{thm:stationary-rational-diagonal-namecert-obligation-surface}
The local $\NameCert_{\StationaryRationalDiagonalUp}$ surface consists exactly
of five rows:
\begin{enumerate}
\item carrier: the finite packet of
\autoref{def:stationary-rational-diagonal-carrier};
\item classifier: comparison of two accepted packets through their displayed
$\RatUp$ seed classifier and the induced constant $\StreamNameUp$,
$\RegSeqRatUp$, and $\RealUp$ rows;
\item stability: componentwise $\hsame$ transport and visible $\Cont$ routing
preserve the stationary seed, every constant window, the diagonal selector, and
the real seal ledger;
\item exactness/readback: every consumer read factors through the same
stationary rational seed and the same constant regular-rational window before
it reaches the $\RealUp$ seal;
\item ledger: the $\Pkg$ and $\NameCert$ coordinates expose only $\RatUp$,
$\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$,
$\Cont$, and local certificate rows.
\end{enumerate}
No row of the surface is a quotient, a choice principle, or a host real
equality.
\end{theorem}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_namecert\_obligation\_surface}
\begin{proof}
Project the carrier of
\autoref{def:stationary-rational-diagonal-carrier}. The listed coordinates
already name the rational seed, constant stream, stationary regular readback,
diagonal selector, real seal, transports, continuation routes, package
provenance, and local ledger.

For the classifier row, compare two packets only by the seed classifier and its
constant readbacks. The $\StreamNameUp$ and $\RegSeqRatUp$ coordinates are
stationary, so every selected window reads the same rational row before the
$\RealUp$ seal is consulted.

Stability follows by transporting each visible coordinate through its stored
$\hsame$ row and using the displayed $\Cont$ routes to reach the same selected
window after transport. The exactness row is then forced, because the real seal
has no source except the stationary rational readback.

The ledger is exhausted by $P$ and $N$. Since the carrier has no coordinate for
quotient streams, host real equality, or a hidden selected limit, none of those
objects can be exported by the local certificate.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_semantic\_name\_certificate}

\begin{theorem}[Stationary rational diagonal Real handoff]
\label{thm:stationary-rational-diagonal-real-handoff}
Every accepted $\StationaryRationalDiagonalUp$ packet determines a concrete
$\RealUp$ consumer surface for the stationary rational diagonal representative.
The consumer route reads the $\RatUp$ seed through the constant
$\StreamNameUp$ schedule, the stationary $\RegSeqRatUp$ row, the diagonal
selector, and the displayed $\RealUp$ seal ledger, with all replacements
accounted for by visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Start with the accepted carrier and read its constant stream coordinate. Every
requested observation reaches the same $\RatUp$ seed through the displayed
$\Cont$ route.

The stationary $\RegSeqRatUp$ coordinate repackages those constant observations
as the regular-rational readback used by the diagonal selector. Since the
selector always chooses the stationary member, the selected window and the
regular readback stay on the listed finite rows.

Finally read the $\RealUp$ seal ledger. It is attached to the same stationary
readback and is transported only through the displayed $\hsame$ rows. Repacking
these coordinates gives the real-facing handoff, and the carrier contains no
additional endpoint object.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_real\_handoff}

\begin{theorem}[Stationary rational diagonal consumer boundary]
\label{thm:stationary-rational-diagonal-consumer-boundary}
Every $\RealUp$ or completion-facing consumer of an accepted
$\StationaryRationalDiagonalUp$ packet factors through the finite rows listed
in \autoref{def:stationary-rational-diagonal-carrier}. In particular, the
consumer may use the $\RatUp$ seed, constant $\StreamNameUp$ schedule,
stationary $\RegSeqRatUp$ readback, diagonal selector, $\RealUp$ seal ledger,
visible $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance, and
local $\NameCert$ row, and nothing outside that finite packet.
\end{theorem}
\begin{proof}
Use the obligation surface of
\autoref{thm:stationary-rational-diagonal-namecert-obligation-surface} to
place the carrier, classifier, stability, readback, and ledger rows on one
local certificate surface.

Next apply the handoff of
\autoref{thm:stationary-rational-diagonal-real-handoff}. It routes every
real-facing read through the stationary seed, the constant stream schedule, the
regular-rational readback, the diagonal selector, and the real seal ledger.

It remains to delimit completion-facing consumers. Such a consumer reaches the
packet only through the same $\RealUp$ seal-facing route and the same displayed
provenance rows. Therefore the consumer boundary is exactly the finite packet
surface stated in the theorem, with no coordinate for quotient equality,
choice, or host real equality.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_consumer\_boundary}

\begin{theorem}[Stationary rational diagonal scoped boundary]
\label{thm:stationary-rational-diagonal-scoped-boundary}
The carrier definition, NameCert obligation surface, Real handoff, and consumer
boundary for $\StationaryRationalDiagonalUp$ form a single scoped dependency
packet over exactly the $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$,
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed in
\autoref{def:stationary-rational-diagonal-carrier}. Every accepted consumer
read is routed through that finite packet, and the packet exports no quotient
stream, host real equality, or selected limit.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:stationary-rational-diagonal-carrier} lists the
only coordinates available to the local certificate: the rational seed,
constant stream schedule, stationary regular-rational readback, diagonal
selector, real seal ledger, visible transports, visible continuation routes,
package provenance, and local NameCert row.

The obligation surface of
\autoref{thm:stationary-rational-diagonal-namecert-obligation-surface} makes
those coordinates into the full certificate interface. Its carrier,
classifier, stability, exactness, and ledger rows mention precisely the same
dependency names, so no consumer can acquire an additional source row through
the certificate laws.

The handoff theorem
\autoref{thm:stationary-rational-diagonal-real-handoff} routes every real-facing
read through the constant stream, the stationary regular readback, the diagonal
selector, and the real seal. The consumer boundary theorem
\autoref{thm:stationary-rational-diagonal-consumer-boundary} then applies the
same routing to completion-facing consumers.

Thus every permitted read has already passed through the displayed finite
packet. Since none of the cited rows contains a coordinate for quotient streams,
host real equality, or a selected limit, none of those objects is exported by
the scoped boundary.
\end{proof}

\begin{theorem}[Stationary rational diagonal classifier determinacy]
\label{thm:stationary-rational-diagonal-classifier-determinacy}
Let $D$ and $D'$ be accepted $\StationaryRationalDiagonalUp$ packets. If their
displayed $\RatUp$ seed rows classify together on the local carrier, then their
induced constant $\StreamNameUp$ schedules, stationary $\RegSeqRatUp$ windows,
diagonal selector rows, and $\RealUp$ seal routes classify together through the
stored $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. Conversely, any accepted
classifier comparison on those downstream rows restricts to the displayed
rational seed classifier, since the rational seed coordinate is the only
carrier coordinate that supplies rational content to the stationary diagonal
read.
\end{theorem}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_classifier\_determinacy}
\begin{proof}
Project the carriers of $D$ and $D'$ along
\autoref{def:stationary-rational-diagonal-carrier}. The only rational source
row in each packet is the displayed $\RatUp$ seed; the remaining rows are the
constant stream schedule, the stationary regular-rational readback, the
diagonal selector, the real seal ledger, and the visible transport and package
rows.

Stationarity reduces every selected regular-rational window to that same
rational row. Therefore a seed classifier comparison transports directly to
the constant $\StreamNameUp$ schedule and to each stationary $\RegSeqRatUp$
window read through the stored $\hsame$ rows.

Apply the real handoff of
\autoref{thm:stationary-rational-diagonal-real-handoff} and the scoped boundary
of \autoref{thm:stationary-rational-diagonal-scoped-boundary}. The diagonal
selector and $\RealUp$ seal route do not add a second rational source; they
only route the stationary read through the displayed $\Cont$, $\Pkg$, and
$\NameCert$ rows.

For the converse, restrict any accepted downstream classifier comparison back
along the handoff route. The boundary theorem leaves exactly one carrier
coordinate that can supply rational content, namely the displayed seed row, so
the downstream classifier comparison determines the same local $\RatUp$ seed
classifier.
\end{proof}

\begin{theorem}[Stationary rational diagonal constant-window totality]
\label{thm:stationary-rational-diagonal-constant-window-totality}
Every unary request made against an accepted $\StationaryRationalDiagonalUp$
packet reads the same displayed $\RatUp$ row. The read first follows the
constant $\StreamNameUp$ schedule generated by the seed, then the stationary
$\RegSeqRatUp$ window row, and then the diagonal selector that returns that
stationary window for the requested precision.

Thus every consumer-visible rational observation is already the displayed seed
row, transported only through the listed $\mathsf{BHist}$, $\hsame$, $\Cont$,
$\Pkg$, and $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_constant\_window\_totality}
\begin{proof}
Project the accepted carrier along
\autoref{def:stationary-rational-diagonal-carrier}. Its only rational coordinate
is the seed $q$, and its stream coordinate $C$ is explicitly the constant
schedule generated by $q$.

Read a unary request through the continuation route $K$. The schedule therefore
returns the same rational row for the requested place, and the stationary
$\RegSeqRatUp$ coordinate $R$ records that every displayed regular window has
that same readback.

Finally apply the diagonal selector coordinate $D$. Since $D$ always selects the
stationary member and the requested regular-sequence window, no second rational
row can be introduced. The transport and provenance coordinates merely move the
same displayed rows, so the readback is total on the stated finite surface.
\end{proof}

\begin{theorem}[Stationary rational diagonal seal factorization]
\label{thm:stationary-rational-diagonal-seal-factorization}
For every accepted $\StationaryRationalDiagonalUp$ packet, the $\RealUp$ seal
ledger factors only through the displayed $\RatUp$ seed, constant
$\StreamNameUp$ schedule, stationary $\RegSeqRatUp$ readback, diagonal selector,
and visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

In particular, the seal cannot factor through quotient regular streams, a host
real equality, an ambient completeness principle, or a selected limit outside
the carrier.
\end{theorem}
\begin{proof}
Start from the real handoff theorem
\autoref{thm:stationary-rational-diagonal-real-handoff}. It identifies the
seal-facing route as the route from the rational seed through the constant
stream, stationary regular readback, diagonal selector, and real seal ledger.

Use the constant-window totality theorem
\autoref{thm:stationary-rational-diagonal-constant-window-totality} to collapse
each unary read on that route to the same displayed $\RatUp$ seed row. The
$\RealUp$ seal is therefore reached after a finite readback path whose source is
the carrier coordinate $q$.

The remaining carrier coordinates are $H$, $K$, $P$, and $N$. These record
transport, continuation, package provenance, and local certificate provenance;
they do not contain quotient regular streams, host real equality, ambient
completeness, or selected limits. Hence the stated factorization exhausts the
seal ledger.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_seal\_factorization}

\begin{theorem}[Stationary rational diagonal obligation-closure package]
\label{thm:stationary-rational-diagonal-obligation-closure-package}
The $\StationaryRationalDiagonalUp$ carrier, NameCert surface, Real handoff,
consumer boundary, scoped boundary, classifier determinacy, constant-window
totality, and seal factorization assemble an obligation-closed paper package.
Its closed scope is exactly the displayed $\RatUp$, $\StreamNameUp$,
$\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and
$\NameCert$ dependency surface.
\end{theorem}
\begin{proof}
The carrier definition supplies the finite packet and its dependency names. The
NameCert obligation surface records the carrier, classifier, stability,
readback, and ledger rows on that packet.

The Real handoff and consumer boundary route all real-facing and
completion-facing reads through the same finite coordinates. The scoped boundary
then states that no additional quotient, host equality, or selected limit is
available to consumers.

Classifier determinacy identifies the accepted comparison with the displayed
rational seed classifier and its transported downstream rows. Constant-window
totality and seal factorization complete the package by showing that every unary
read and every real-seal read is exhausted by the same stationary rational
route. These rows are precisely the named obligation surface, so the paper-side
closure grade is obligation closure.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_obligation\_closure\_package}

\closureat{StationaryRationalDiagonalUp}{seedStr}
\closureat{StationaryRationalDiagonalUp}{obligationStr}
\closureat{StationaryRationalDiagonalUp}{scopedStr}[BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_seal\_factorization]

\begin{closurestatus}{\StationaryRationalDiagonalUp}
  \constructivestory{A $\StationaryRationalDiagonalUp$ packet is generated from one $\RatUp$ source row, its constant $\StreamNameUp$ schedule, a stationary $\RegSeqRatUp$ readback, a diagonal selector, a $\RealUp$ seal ledger, visible $\hsame$ and $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{thm:stationary-rational-diagonal-consumer-boundary} binds the finite stationary rational diagonal carrier, NameCert surface, Real handoff, and consumer boundary over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.StationaryRationalDiagonalUp.StationaryRationalDiagonalCarrier\_seal\_factorization}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close general real completeness, arbitrary regular Cauchy sequences, quotient equality of regular streams, uniqueness of limits, host real construction, or bridge checking.}
  \upgradepath{Public closure requires a public-object boundary for stationary rational diagonal consumers beyond the scoped seal factorization.}
\end{closurestatus}
