\begin{theorem}[LieGroup singleton source lock]
\label{thm:liegroup-singleton-source-lock}
The singleton $\LieGroupUp$ source uses the single predicate
$L_{\emp}(h):\Longleftrightarrow \hsame(h,\emp)$ as the $\GroupUp$ carrier,
the $\ManifoldUp$ point and chart-domain carrier, and the $\LieGroupUp$
carrier. Its classifier is the same restricted $\hsame$ row
$R_{\emp}(h,k)$ from \autoref{def:liegroup-singleton-smooth-group-carrier};
no transported second source, auxiliary carrier, or duplicate classifier is
introduced.
\end{theorem}
\begin{proof}
Unfold \autoref{def:liegroup-singleton-smooth-group-carrier}. The displayed
predicate $L_{\emp}$ is the only carrier predicate named there, and the
classifier is the displayed restricted row $R_{\emp}$.

Project the singleton group rows from
\autoref{thm:group-singleton-history-semantic-namecert}. These rows use
$\mathsf{BHist}$, $\emp$, $\mathsf{append}$, constant inverse, and the
restricted $\hsame$ classifier; their checked source is
$\mathsf{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}$.

Project the singleton chart rows from
\autoref{thm:manifold-singleton-namecert-obligation-package}. The chart
domain is the same predicate $\hsame(h,\emp)$, the chart value is constant,
and the overlap row is the singleton transition row.

Thus both projected packages identify their visible carrier with
$L_{\emp}$. The $\LieGroupUp$ package is assembled by sharing that predicate
and classifier rather than by transporting data across a second source.
\end{proof}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_source\_lock}

\begin{theorem}[LieGroup singleton exact ledger]
\label{thm:liegroup-singleton-exact-ledger}
For the singleton $\LieGroupUp$ package, the accepted ledger consists exactly
of $\mathsf{BHist}$, $\hsame$, $\emp$, $\mathsf{append}/\Cont$, the singleton
$\GroupUp$ laws, the singleton chart domain and chart value, and the
singleton constant transition row. It excludes any standard bridge, any host
smooth-manifold equality, any extra carrier, and any external topology row.
\end{theorem}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_exact\_ledger}
\begin{proof}
The source-lock theorem fixes the boundary of the ledger: all carrier and
classifier rows are projections of the one history predicate $L_{\emp}$ and
the restricted $\hsame$ relation.

The algebraic entries are exactly the singleton $\GroupUp$ rows. They are
supplied by \autoref{thm:group-singleton-history-semantic-namecert} and
$\mathsf{BEDC.Derived.GroupUp.GroupSingletonHistory\_laws}$, namely
$\mathsf{BHist}$, $\hsame$, $\emp$, $\mathsf{append}$, $\Cont$, and the
singleton group laws.

The smooth entries are exactly the singleton $\ManifoldUp$ rows. They are
supplied by \autoref{thm:manifold-singleton-namecert-obligation-package},
$\mathsf{BEDC.Derived.ManifoldUp.ManifoldSingleton\_semanticNameCert}$, and
$\mathsf{BEDC.Derived.ManifoldUp.ManifoldSingleton\_transition\_smoothness}$:
the singleton chart domain, constant chart value, and constant transition.

Finally,
\autoref{thm:liegroup-singleton-operation-smoothness-obligation} accounts for
the operation rows by reading multiplication and inverse through the same
singleton atlas. No cited row provides a $\StdBridge$, host equality of smooth
manifolds, an additional carrier predicate, or an external topology, so none
belongs to the accepted ledger.
\end{proof}

\begin{theorem}[LieGroup singleton downstream export]
\label{thm:liegroup-singleton-downstream-export}
The packages $\ExpMapUp$, $\AdjointRepUp$, $\RootSystemUp$, and
representation certificates may consume the singleton $\LieGroupUp$ package
only through the exported carrier, classifier, operation, chart, and
transition rows. The singleton package makes no downstream claim of
connectedness, completeness, nontrivial Lie algebra, or standard bridge.
\end{theorem}
\begin{proof}
By \autoref{thm:liegroup-singleton-source-lock}, every visible carrier and
classifier row of the singleton $\LieGroupUp$ package is a projection of the
shared history predicate $L_{\emp}$ and the restricted $\hsame$ classifier.
These are the only source rows a dependent certificate can name.

By \autoref{thm:liegroup-singleton-exact-ledger}, the remaining visible rows
are precisely the group operation rows, singleton chart rows, and singleton
transition row. The NameCert surface in
\autoref{thm:liegroup-singleton-namecert-obligation} repacks those rows as the
public obligation surface for $\LieGroupUp$.

Therefore any $\ExpMapUp$, $\AdjointRepUp$, $\RootSystemUp$, or
representation certificate built over this singleton source can project only
those exported rows. Since the ledger contains no connectedness, completeness,
nontrivial Lie-algebra, or $\StdBridge$ row, no downstream consumer receives
such a claim from this package.
\end{proof}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_downstream\_export}

\begin{definition}[Singleton LieGroup conjugation action]
\label{def:liegroup-singleton-conjugation-action}
On the singleton smooth group carrier
\autoref{def:liegroup-singleton-smooth-group-carrier}, define the
$\mathsf{BHist}$-valued conjugation action by
$$
\mathsf{Ad}_{\emp}(s,x):=
\mathsf{append}(\mathsf{append}(s,x),\emp).
$$
The inputs are carried histories $L_{\emp}(s)$ and $L_{\emp}(x)$, and the
terminal factor $\emp$ is the singleton inverse row of the group carrier.
\end{definition}
\leandef{BEDC.Derived.LieGroupUp.LieGroupSingletonConjugationAction}

\begin{theorem}[LieGroup singleton conjugation carrier and smoothness]
\label{thm:liegroup-singleton-conjugation-carrier-and-smoothness}
If $L_{\emp}(s)$ and $L_{\emp}(x)$ hold, then
$\mathsf{Ad}_{\emp}(s,x)$ is again carried by $L_{\emp}$. Moreover the singleton
manifold chart reads this conjugation endpoint as the same constant smooth
transition that reads multiplication and inverse in
\autoref{thm:liegroup-singleton-operation-smoothness-obligation}.
\end{theorem}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_conjugation\_carrier\_and\_smoothness}
\begin{proof}
Unfold \autoref{def:liegroup-singleton-conjugation-action}. The endpoint is the
append-composite $(s*x)*\emp$ in the singleton group rows. Since $s$ and $x$ are
carried, \autoref{thm:group-singleton-history-semantic-namecert} gives closure
of $s*x$, and the right multiplication by $\emp$ stays in the same carrier. The
Lean-side row
$\mathsf{BEDC.Derived.GroupUp.GroupSingletonClassifier\_conjugation\_terminal\_collapse\_iff}$
records the same terminal collapse for the singleton classifier.

For smoothness, the carried input pair and the carried output all lie in the
sole singleton chart domain. Applying
\autoref{thm:manifold-singleton-transition-smoothness} reads the source and
target charts as the constant value $0_{\RealUp}$, so the displayed action has
the constant smooth transition row already used by the multiplication and
inverse obligations. The corresponding Lean-side row is
$\mathsf{BEDC.Derived.ManifoldUp.ManifoldSingleton\_transition\_smoothness}$.
\end{proof}

\begin{theorem}[LieGroup singleton conjugation action law]
\label{thm:liegroup-singleton-conjugation-action-law}
For carried histories $L_{\emp}(s)$, $L_{\emp}(t)$, and $L_{\emp}(x)$, the two
iterated endpoints
$$
\mathsf{Ad}_{\emp}(s,\mathsf{Ad}_{\emp}(t,x))
$$
and
$$
\mathsf{Ad}_{\emp}(\mathsf{append}(s,t),x)
$$
are both classified by the singleton classifier $R_{\emp}$, hence represent the
same carried singleton endpoint.
\end{theorem}
\begin{proof}
First unfold the action on the left. The inner endpoint is
$\mathsf{append}(\mathsf{append}(t,x),\emp)$, and
\autoref{thm:liegroup-singleton-conjugation-carrier-and-smoothness} carries it
back into $L_{\emp}$. Applying the same theorem to $s$ and this inner endpoint
therefore carries the whole left-hand endpoint.

Next unfold the action on the right. Group singleton closure carries
$\mathsf{append}(s,t)$, and another application of
\autoref{thm:liegroup-singleton-conjugation-carrier-and-smoothness} carries
$\mathsf{Ad}_{\emp}(\mathsf{append}(s,t),x)$.

It remains to compare the classifier rows. By the singleton group classifier,
every carried endpoint is $\hsame$ to $\emp$. The $\Cont$ associativity and
readback rows allow the nested append words on both sides to be read as
singleton terminal words, and the group singleton closure removes the terminal
factor. Thus both displayed endpoints satisfy $R_{\emp}$ against $\emp$, and
therefore against each other by the restricted singleton classifier.
\end{proof}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_conjugation\_action\_law}

\begin{theorem}[LieGroup singleton AdjointRep source surface]
\label{thm:liegroup-singleton-adjointrep-source-surface}
The rows of
\autoref{def:liegroup-singleton-conjugation-action},
\autoref{thm:liegroup-singleton-conjugation-carrier-and-smoothness}, and
\autoref{thm:liegroup-singleton-conjugation-action-law} supply the
$\LieGroupUp$-side source surface consumed by $\AdjointRepUp$: the operation
$\mathsf{Ad}_{\emp}$ is $\mathsf{BHist}$-valued, classifier-stable on the
singleton carrier, smooth in the singleton atlas, and carries no standard bridge
row.
\end{theorem}
\begin{proof}
The definition provides the concrete $\mathsf{BHist}$ operation. The carrier and
smoothness theorem supplies the two structural rows needed by a representation
source: accepted inputs give an accepted endpoint, and the singleton atlas reads
that endpoint through the constant smooth transition.

The action-law theorem supplies the compatibility row. Both iterated
conjugation and conjugation by the product word land in the singleton classifier
class, so $\AdjointRepUp$ can consume the action without adding a separate
carrier transport or chart transition.

No standard bridge row is part of this surface. The package is only the
paper-side singleton $\LieGroupUp$ action source over $\mathsf{BHist}$, with the
ordinary Lie-group bridge left outside the displayed rows.
\end{proof}
\leanchecked{BEDC.Derived.LieGroupUp.LieGroupSingleton\_adjointrep\_source\_surface}
