\chapter{A Concrete Naming Certificate for $\StationaryRationalCauchyUp$}
\label{ch:concrete-instances-stationary-rational-cauchy-namecert}
\origin{human}

The $\StationaryRationalCauchyUp$ interface records the concrete stationary rational regular Cauchy input that appears in \autoref{def:real-completeness-stationary-rational-cauchy}. It is the finite $\RealUp$ handoff certificate obtained by keeping the hidden $\RatUp$ seed, its constant $\StreamNameUp$ windows, the associated $\RegSeqRatUp$ member, the $\DyadicRatCoreUp$ observation ledger, and the local $\Pkg$ and $\NameCert$ rows visible.

The chapter consumes the diagonal representative supplied by \autoref{ch:concrete-instances-stationaryrationaldiagonal-namecert} and narrows it to the stationary rational Cauchy packet through the displayed $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ ledger. The dependency is substantive: the RealUp handoff below is the constant rational diagonal read with every non-stationary coordinate removed.

\begin{definition}[StationaryRationalCauchy carrier]
\label{def:stationary-rational-cauchy-carrier}
A $\StationaryRationalCauchyUp$ carrier is a finite $\BHist$ packet
$$
S=(q,A,R,D,E,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $q$ is the hidden $\RatUp$ row supplying the rational seed;
\item $A$ is the constant $\StreamNameUp$ schedule whose every requested finite window reads the seed $q$;
\item $R$ is the stationary $\RegSeqRatUp$ member whose every regular-sequence index returns the stream row $A$ with the zero modulus row;
\item $D$ is the $\DyadicRatCoreUp$ ledger recording the same rational observation at every selected window;
\item $E$ is the $\RealUp$ seal row for the constant rational embedding of $q$;
\item $P$ is the $\Pkg$ provenance row naming the $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\NameCert$ dependencies;
\item $N$ is the local $\NameCert_{\StationaryRationalCauchyUp}$ row.
\end{enumerate}
The local classifier compares two carriers by the displayed $\hsame$ transport of the seed rows, constant stream schedules, stationary regular-sequence members, dyadic ledgers, real seals, package provenance, and local certificate rows, with $\Cont$ routes recording the finite-window readback used by each consumer.
\end{definition}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyTasteGate\_single\_carrier\_alignment}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyUpTasteGate\_single\_carrier\_alignment\_ChapterTasteGate}

\begin{theorem}[StationaryRationalCauchy NameCert obligations]
\label{thm:stationary-rational-cauchy-namecert-obligations}
The $\NameCert_{\StationaryRationalCauchyUp}$ surface consists of four obligations over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows: carrier habitation by \autoref{def:stationary-rational-cauchy-carrier}; constant-stream classifier reflexivity for the $\RatUp$ seed inside every $\StreamNameUp$ window; stationary $\RegSeqRatUp$ stability with the zero modulus and the same $\DyadicRatCoreUp$ observation ledger; and exact export of the constant rational $\RealUp$ seal without quotient stream equality, selected host limits, or ambient real completeness.
\end{theorem}
\begin{proof}
Carrier habitation is the finite packet assembly. The seed row, constant stream schedule, stationary regular-sequence member, dyadic observation ledger, real seal, package provenance, and local certificate row are all visible coordinates of the $\BHist$ carrier.

Constant-stream reflexivity supplies the classifier row: each $\StreamNameUp$ window reads the same $\RatUp$ seed, so its $\hsame$ comparison is the reflexive comparison transported along the displayed $\Cont$ route for that finite window.

The regular Cauchy obligation is stationary. The zero modulus row is admissible because every member of the $\RegSeqRatUp$ family returns the same stream row and the same $\DyadicRatCoreUp$ rational observation ledger.

The export obligation is ledger exactness. The $\Pkg$ and $\NameCert$ rows name exactly the dependency certificates used in the readback, and no field of the carrier contains a quotient of streams, a selected host limit, or an ambient completeness object.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_namecert\_obligations}

\begin{theorem}[StationaryRationalCauchy diagonal handoff]
\label{thm:stationary-rational-cauchy-diagonal-handoff}
For every accepted $\StationaryRationalCauchyUp$ carrier $S$ and every unary precision request $n$, the diagonal read used by the $\RealUp$ handoff factors through the stationary $\RegSeqRatUp$ member of $S$, one finite constant $\StreamNameUp$ window, the $\RatUp$ seed row, the matching $\DyadicRatCoreUp$ observation ledger, and the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows carried by $S$.
\end{theorem}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyBHistCarrier\_diagonal\_handoff}
\begin{proof}
Project the packet of \autoref{def:stationary-rational-cauchy-carrier}. The requested precision $n$ reaches the stationary regular-sequence member $R$, and $R$ returns the same stream row at every index.

Read the scheduled finite window of $A$. Because $A$ is constant, the selected window returns the seed row $q$ with the same $\DyadicRatCoreUp$ observation ledger independently of $n$.

The displayed $\hsame$ comparison transports this read through the stored $\Cont$ route, and the $\Pkg$ and $\NameCert$ rows record the provenance of the read. Thus the diagonal read is exactly the finite route listed in the statement.
\end{proof}

\begin{theorem}[StationaryRationalCauchy finite-prefix uniformity]
\label{thm:stationary-rational-cauchy-finite-prefix-uniformity}
For every accepted $\StationaryRationalCauchyUp$ carrier $S=(q,A,R,D,E,P,N)$ and every finite unary prefix of precision requests, each request in the prefix reads the same $\RatUp$ seed $q$ through the same constant $\StreamNameUp$ schedule $A$, the same stationary $\RegSeqRatUp$ member $R$, and the same $\DyadicRatCoreUp$ ledger $D$. The only variation permitted across the prefix is the displayed $\hsame$ transport and $\Cont$ route used to reach the repeated rows.
\end{theorem}
\begin{proof}
Induct over the finite prefix. The empty prefix has no requested read, so the carrier coordinates already supply the uniform seed, schedule, regular-sequence member, and ledger.

For a prefix extended by one request $n$, apply \autoref{thm:stationary-rational-cauchy-diagonal-handoff} to the final request. The handoff routes $n$ through $R$, then through the constant schedule $A$, and then back to the seed row $q$ and ledger $D$.

The induction hypothesis gives the same rows for the earlier requests. Since the carrier of \autoref{def:stationary-rational-cauchy-carrier} is stationary in $q,A,R,D$, the final request introduces no new stream schedule, regular-sequence member, or dyadic ledger. Its displayed $\hsame$ and $\Cont$ rows are the only request-indexed data.
\end{proof}

\begin{theorem}[StationaryRationalCauchy classifier correspondence]
\label{thm:stationary-rational-cauchy-classifier-correspondence}
Let $S=(q,A,R,D,E,P,N)$ and $S'=(q',A',R',D',E',P',N')$ be accepted $\StationaryRationalCauchyUp$ carriers. The local classifier relates $S$ and $S'$ exactly when the displayed $\RatUp$ classifier relates $q$ and $q'$ and the associated $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\Pkg$, and $\NameCert$ rows are transported componentwise by the recorded $\hsame$ comparisons and $\Cont$ routes.
\end{theorem}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_classifier\_correspondence}
\begin{proof}
For the forward direction, inspect the local classifier. Its only seed-sensitive coordinate is the hidden rational row, and every stream, regular-sequence, dyadic, real-seal, package, and certificate coordinate is defined as the stationary readback of that seed. Projecting the classifier therefore gives the displayed $\RatUp$ comparison and the componentwise transport rows.

For the reverse direction, start with the $\RatUp$ comparison between $q$ and $q'$. Constant-stream reflexivity transports it to every finite $\StreamNameUp$ window of $A$ and $A'$.

The same finite-window transport lifts to the stationary $\RegSeqRatUp$ members because all regular-sequence indices read those constant stream rows. The $\DyadicRatCoreUp$ ledgers and $\RealUp$ seals are then the diagonal readbacks of the same transported windows.

Repack the transported coordinates with $P,P'$ and $N,N'$. Since the local classifier compares exactly these rows, the two carriers are classified together.
\end{proof}

\begin{theorem}[StationaryRationalCauchy ledger exactness]
\label{thm:stationary-rational-cauchy-ledger-exactness}
Every consumer-facing $\RealUp$ read exported by an accepted $\StationaryRationalCauchyUp$ carrier is exhausted by the finite ledger
$$
\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \DyadicRatCoreUp \to \RealUp
$$
together with the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The carrier exports no additional equality principle, host-real endpoint, non-stationary Cauchy family, or completeness theorem.
\end{theorem}
\begin{proof}
Begin with the diagonal handoff of \autoref{thm:stationary-rational-cauchy-diagonal-handoff}. It shows that each consumer read first reaches the stationary $\RegSeqRatUp$ member and then a finite constant $\StreamNameUp$ window.

The window read returns the hidden $\RatUp$ seed and the matching $\DyadicRatCoreUp$ observation. The $\RealUp$ seal row is attached to that same constant rational readback.

The remaining carrier coordinates are provenance: $\BHist$ supplies the finite packet, $\hsame$ and $\Cont$ supply the visible transports, and $\Pkg$ and $\NameCert$ name the certificate rows. These fields exhaust the exported ledger, so no further equality principle, host-real endpoint, non-stationary family, or completeness theorem is available from the carrier.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_ledger\_exactness}

\begin{theorem}[StationaryRationalCauchy RegSeqRat handoff scope]
\label{thm:stationary-rational-cauchy-regseqrat-handoff-scope}
The constant rational embedding carried by $\StationaryRationalCauchyUp$ into $\RegSeqRatUp$ and $\RealUp$ is scoped entirely by the displayed $\RatUp$ seed, constant $\StreamNameUp$ schedule, stationary $\RegSeqRatUp$ member, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It does not require quotient stream equality, selected host limits, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with the carrier of \autoref{def:stationary-rational-cauchy-carrier}. Its finite packet exposes the seed $q$, constant schedule $A$, stationary member $R$, dyadic ledger $D$, real seal $E$, package row $P$, and local certificate row $N$.

The diagonal handoff of \autoref{thm:stationary-rational-cauchy-diagonal-handoff} sends each precision request through $R$ and then through a finite window of $A$ back to $q$ and $D$. The finite-prefix uniformity of \autoref{thm:stationary-rational-cauchy-finite-prefix-uniformity} shows that repeating the read across any finite request list introduces no new stream schedule, regular-sequence member, or ledger.

Classifier correspondence in \autoref{thm:stationary-rational-cauchy-classifier-correspondence} transports exactly the displayed seed, stream, regular-sequence, dyadic, real, package, and certificate rows. Ledger exactness from \autoref{thm:stationary-rational-cauchy-ledger-exactness} then exhausts the exported $\RealUp$ read, excluding quotient stream equality, selected host limits, and ambient completeness from the handoff scope.
\end{proof}
\leanchecked{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyUp\_StdBridge}

\begin{theorem}[StationaryRationalCauchy RealUp embedding exactness]
\label{thm:stationary-rational-cauchy-real-embedding-exactness}
For every accepted $\StationaryRationalCauchyUp$ carrier $S=(q,A,R,D,E,P,N)$, the exported $\RealUp$ seal $E$ is exactly the constant rational embedding route through the $\RatUp$ seed $q$, the constant $\StreamNameUp$ schedule $A$, the stationary $\RegSeqRatUp$ member $R$, the $\DyadicRatCoreUp$ ledger $D$, and the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Equivalently, every consumer read of $E$ is exhausted by the finite route
$$
\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \DyadicRatCoreUp \to \RealUp
$$
inside the carrier $S$. The exported seal does not use quotient stream equality, a selected host limit, or ambient completeness.
\end{theorem}
\begin{proof}
First read the diagonal route. By \autoref{thm:stationary-rational-cauchy-diagonal-handoff}, every precision request reaches the stationary member $R$, then a finite constant window of $A$, and then the seed row $q$ with the matching ledger $D$.

Next make the route uniform. The finite-prefix uniformity theorem shows that any finite family of requests reads the same $q$, $A$, $R$, and $D$ rows. Thus the $\RealUp$ seal cannot depend on a non-stationary stream coordinate.

Transport and exactness are then componentwise. Classifier correspondence moves exactly the displayed seed, stream, regular-sequence, dyadic, seal, package, and certificate rows, while ledger exactness exhausts the $\RealUp$ read by the finite chain shown above.

Finally apply the RegSeqRat handoff scope theorem. It identifies the same stationary route as the entire $\RegSeqRatUp$ and $\RealUp$ handoff, so $E$ is precisely the constant rational embedding of $q$ and not a quotient stream, selected host limit, or ambient completeness construction.
\end{proof}

\begin{theorem}[StationaryRationalCauchy obligation package]
\label{thm:stationary-rational-cauchy-obligation-package}
For every accepted $\StationaryRationalCauchyUp$ carrier $S=(q,A,R,D,E,P,N)$, the obligation package is the finite package assembled from the carrier, the $\NameCert$ obligations, the diagonal handoff, finite-prefix uniformity, classifier correspondence, ledger exactness, $\RegSeqRatUp$ handoff scope, and $\RealUp$ embedding exactness rows. Its visible coordinates are the hidden $\RatUp$ seed $q$, constant $\StreamNameUp$ schedule $A$, stationary $\RegSeqRatUp$ member $R$, $\DyadicRatCoreUp$ ledger $D$, $\RealUp$ seal $E$, package row $P$, local $\NameCert$ row $N$, and the displayed $\BHist$, $\hsame$, and $\Cont$ witnesses.
\end{theorem}
\begin{proof}
First project the carrier and the local certificate obligations from \autoref{def:stationary-rational-cauchy-carrier} and \autoref{thm:stationary-rational-cauchy-namecert-obligations}. These rows provide the seed, constant schedule, stationary member, dyadic ledger, real seal, package provenance, local name, and transport witnesses.

Next assemble the finite request behavior. The diagonal handoff sends each precision request through $R$, $A$, $q$, and $D$, while finite-prefix uniformity shows that finite request lists reuse the same stationary rows.

Finally add the classifier, ledger, handoff, and embedding rows. \autoref{thm:stationary-rational-cauchy-classifier-correspondence}, \autoref{thm:stationary-rational-cauchy-ledger-exactness}, \autoref{thm:stationary-rational-cauchy-regseqrat-handoff-scope}, and \autoref{thm:stationary-rational-cauchy-real-embedding-exactness} identify the same finite stationary package as the full obligation surface.
\end{proof}

\begin{theorem}[StationaryRationalCauchy stationary readback]
\label{thm:stationary-rational-cauchy-stationary-readback}
Every stationary readback from an accepted $\StationaryRationalCauchyUp$ carrier factors through the hidden $\RatUp$ seed $q$, constant $\StreamNameUp$ windows $A$, stationary $\RegSeqRatUp$ member $R$, $\DyadicRatCoreUp$ ledger $D$, package row $P$, local $\NameCert$ row $N$, and the displayed $\BHist$, $\hsame$, and $\Cont$ rows. No readback introduces a non-stationary stream, quotient stream equality, selected host limit, or ambient completeness datum.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:stationary-rational-cauchy-diagonal-handoff}. A precision request reaches $R$, then the constant window $A$, then the seed $q$ and dyadic ledger $D$.

Use \autoref{thm:stationary-rational-cauchy-finite-prefix-uniformity} for multiple requests. The same $q,A,R,D$ rows serve every finite prefix, so no new stream schedule or regular-sequence member appears.

Finally apply \autoref{thm:stationary-rational-cauchy-classifier-correspondence}. The package, certificate, $\BHist$, $\hsame$, and $\Cont$ rows transport the same stationary data componentwise, preserving the exclusions in the statement.
\end{proof}

\begin{theorem}[StationaryRationalCauchy RealUp seal non-escape]
\label{thm:stationary-rational-cauchy-real-seal-non-escape}
The $\RealUp$ seal exported by an accepted $\StationaryRationalCauchyUp$ carrier does not provide quotient Cauchy classes, host sequence equality, selected limits, or ambient completeness. It is exactly the finite stationary route through the $\RatUp$ seed, constant $\StreamNameUp$ windows, stationary $\RegSeqRatUp$ member, $\DyadicRatCoreUp$ ledger, $\Pkg$ provenance, $\NameCert$ row, and displayed $\BHist$, $\hsame$, and $\Cont$ witnesses.
\end{theorem}
\begin{proof}
First read the seal through \autoref{thm:stationary-rational-cauchy-real-embedding-exactness}. The seal is the constant rational embedding route through $q,A,R,D,E,P,N$.

Next use \autoref{thm:stationary-rational-cauchy-ledger-exactness}. Ledger exactness exhausts the $\RealUp$ read by the dyadic observation and stationary rational rows, leaving no coordinate for quotient Cauchy classes or host sequence equality.

Finally apply \autoref{thm:stationary-rational-cauchy-obligation-package}. Since the obligation surface contains only the finite stationary carrier rows and their displayed transports, selected limits and ambient completeness are not exported by the seal.
\end{proof}

\closureat{StationaryRationalCauchyUp}{seedStr}
\closureat{StationaryRationalCauchyUp}{obligationStr}[BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_ledger\_exactness]
\closureat{StationaryRationalCauchyUp}{scopedStr}[BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_ledger\_exactness]

\begin{closurestatus}{\StationaryRationalCauchyUp}
  \constructivestory{A $\StationaryRationalCauchyUp$ packet is generated from a hidden $\RatUp$ seed, a constant $\StreamNameUp$ schedule, a stationary $\RegSeqRatUp$ member, a $\DyadicRatCoreUp$ observation ledger, a $\RealUp$ seal, and displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:stationary-rational-cauchy-carrier} and \autoref{thm:stationary-rational-cauchy-namecert-obligations} bind the $\RatUp$ seed, constant $\StreamNameUp$ schedule, stationary $\RegSeqRatUp$ member, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the stationary rational Cauchy packet.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.StationaryRationalCauchyUp.StationaryRationalCauchyCarrier\_namecert\_obligations}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close the exact kernel dependency scope, public bridge, or completion uniqueness obligations.}
  \upgradepath{The next paper-grade obligation is a public export for the stationary rational $\RealUp$ embedding.}
\end{closurestatus}
