\chapter{A Concrete Naming Certificate for $\TailCompatibleCauchySectionUp$}
\label{ch:concrete-instances-tailcompatiblecauchysection-namecert}
\origin{ai-composite}

The $\TailCompatibleCauchySectionUp$ packet realizes the finite-window route behind the regular-Cauchy diagonal-limit construction of \autoref{ch:visions-real-completeness}. It is structurally composite over the stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the dyadic ledgers of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the regular-rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the real-name seal of \autoref{ch:concrete-instances-real-namecert}, and the finite observation-budget selector of \autoref{ch:concrete-instances-finiteobservationbudgetselector-namecert}. The packet names a compatible finite section, not a host limit, quotient stream, selected infinite subsequence, or ambient completeness principle.

Because the carrier is composite over $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, and $\FiniteObservationBudgetSelectorUp$, its falsifiability and independence witnesses are inherited from those component packets. The atomic falsifiability and independence rows used for primitive carriers are therefore not used here.

\begin{definition}[Tail-compatible Cauchy section carrier]
\label{def:tail-compatible-cauchy-section-carrier}
A $\TailCompatibleCauchySectionUp$ carrier is a finite packet
$$
S=(X,\mu,n,k,i,W,B,R,D,E,H,C,P,N)
$$
with the following rows:
\begin{enumerate}
\item $X$ is the displayed regular-Cauchy family from \autoref{sec:real-completeness-regular-cauchy};
\item $\mu$ is the modulus row selecting tail indices for $X$;
\item $n$ is the visible precision request;
\item $k=\mu(1/(n+1))$ and $i=k+n+1$ are the displayed diagonal-section indices;
\item $W$ is the $\StreamNameUp$ finite window exposing the $i$-th read of the $k$-th regular-rational member;
\item $B$ is the $\FiniteObservationBudgetSelectorUp$ budget row certifying that the same window is admissible for the section read;
\item $R$ is the $\RegSeqRatUp$ readback row for the selected regular-rational member along $W$;
\item $D$ is the $\DyadicRatCoreUp$ tolerance and arithmetic ledger attached to the selected readback;
\item $E$ is the $\RealUp$ seal row reached by repacking the selected regular-rational read through the displayed finite route;
\item $H$ records componentwise $\hsame$ transport for $X,\mu,n,k,i,W,B,R,D,E$ and the local certificate row;
\item $C$ records $\Cont$ replay from the precision request through the budgeted window, readback, dyadic ledger, and real seal;
\item $P$ is the $\Pkg$ provenance over $\TailCompatibleCauchySectionUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\FiniteObservationBudgetSelectorUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\TailCompatibleCauchySectionUp}$ row.
\end{enumerate}
The carrier exports only the displayed finite section rows and their transport, replay, provenance, and naming support.
\end{definition}

\begin{definition}[Tail-compatible Cauchy section classifier]
\label{def:tail-compatible-cauchy-section-classifier}
Two accepted $\TailCompatibleCauchySectionUp$ carriers classify together exactly when their regular-Cauchy family rows and modulus rows select the same displayed diagonal-section route, their precision requests yield the same finite index pair $k,i$, and their $\StreamNameUp$, $\FiniteObservationBudgetSelectorUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, transport, continuation, package, and local naming rows are related componentwise by the recorded $\hsame$ comparisons and $\Cont$ routes.
\end{definition}

\begin{theorem}[Tail-compatible Cauchy section NameCert obligations]
\label{thm:tail-compatible-cauchy-section-namecert-obligations}
For the carrier of \autoref{def:tail-compatible-cauchy-section-carrier}, the local $\NameCert_{\TailCompatibleCauchySectionUp}$ surface consists exactly of carrier admission, the finite diagonal-section computations $k=\mu(1/(n+1))$ and $i=k+n+1$, $\StreamNameUp$ window exposure, $\FiniteObservationBudgetSelectorUp$ budget admission, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ tolerance ledger, $\RealUp$ seal exposure, componentwise transport, continuation replay, package provenance, and local naming.
\end{theorem}
\leanchecked{BEDC.Derived.TailCompatibleCauchySectionUp.TailCompatibleCauchySectionTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the packet $S$. Its coordinates list the regular-Cauchy family, modulus, precision request, computed section indices, stream window, budget selector, regular-rational readback, dyadic ledger, real seal, transport, replay, provenance, and local naming rows.

The finite index computation is internal to the packet. The modulus row supplies $k$, the request supplies $n$, and the displayed arithmetic supplies $i=k+n+1$, matching the diagonal representative of \autoref{def:real-completeness-diagonal-limit}.

The remaining rows are precisely the component certificate surfaces. The stream window, budget selector, regular-rational readback, dyadic ledger, and real seal are consumed in that order, while $H,C,P,N$ only transport, replay, source, and name those rows. No further NameCert obligation remains.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section index determinacy]
\label{thm:tail-compatible-cauchy-section-index-determinacy}
For an accepted $\TailCompatibleCauchySectionUp$ carrier
$$
S=(X,\mu,n,k,i,W,B,R,D,E,H,C,P,N),
$$
the displayed regular-Cauchy family row $X$, modulus row $\mu$, and precision request $n$ determine the section route indices. The only admitted route is
$$
k=\mu(1/(n+1))
\qquad\hbox{and}\qquad
i=k+n+1,
$$
followed by the ordered read through $W,B,R,D,E$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:tail-compatible-cauchy-section-carrier}. Its fourth coordinate is the displayed computation of $k$ from the modulus row and the visible precision request, and its fifth coordinate is the displayed computation of $i$ from $k$ and $n$.

The classifier of \autoref{def:tail-compatible-cauchy-section-classifier} admits carriers together only when those same rows select the same diagonal-section route. The obligation theorem \autoref{thm:tail-compatible-cauchy-section-namecert-obligations} then fixes the subsequent order of the stream window, budget row, regular-rational readback, dyadic ledger, and RealUp seal.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section classifier transport]
\label{thm:tail-compatible-cauchy-section-classifier-transport}
Let $S=(X,\mu,n,k,i,W,B,R,D,E,H,C,P,N)$ and $S'=(X',\mu',n',k',i',W',B',R',D',E',H',C',P',N')$ be accepted $\TailCompatibleCauchySectionUp$ carriers. If the recorded componentwise $\hsame$ row relates
$$
X,\mu,n,k,i,W,B,R,D,E
$$
to
$$
X',\mu',n',k',i',W',B',R',D',E',
$$
then the carrier admission and classifier verdict transport from $S$ to $S'$ along the same finite section route.
\end{theorem}
\begin{proof}
Use the transport coordinate $H$ in \autoref{def:tail-compatible-cauchy-section-carrier}. It records the componentwise $\hsame$ comparisons for the regular-Cauchy row, modulus, precision request, index pair, stream window, budget row, readback, dyadic ledger, RealUp seal, and local certificate row.

Apply the classifier definition. Its equality test is not a detached predicate: it is exactly the conjunction of same route selection and componentwise transport through those rows. The NameCert-obligation theorem supplies the carrier admission surface for the transported packet, so the classifier verdict follows with the same ordered route.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section continuation replay]
\label{thm:tail-compatible-cauchy-section-continuation-replay}
For every accepted $\TailCompatibleCauchySectionUp$ packet, any $\Cont$ replay recorded by the carrier preserves the ordered route
$$
W,B,R,D,E.
$$
In particular, the $\RealUp$ seal coordinate $E$ cannot be exposed before the $\StreamNameUp$ window, $\FiniteObservationBudgetSelectorUp$ budget row, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ ledger have been displayed on the same packet.
\end{theorem}
\begin{proof}
Project the continuation coordinate $C$ from the carrier. By \autoref{def:tail-compatible-cauchy-section-carrier}, it replays the precision request through the budgeted stream window, regular-rational readback, dyadic ledger, and RealUp seal in that order.

The NameCert-obligation theorem records the same order as part of the local certificate surface. The seal-boundary theorem \autoref{thm:tail-compatible-cauchy-section-real-seal-boundary} identifies the RealUp-facing boundary as the end of this finite route, so a continuation replay cannot make $E$ available before the component rows $W,B,R,D$ have already appeared.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section component scope binding]
\label{thm:tail-compatible-cauchy-section-component-scope-binding}
Every accepted $\TailCompatibleCauchySectionUp$ packet factors its displayed section route through exactly the component scopes
$$
\StreamNameUp,\ \FiniteObservationBudgetSelectorUp,\ \RegSeqRatUp,\ \DyadicRatCoreUp,\ \RealUp.
$$
The only support rows available to that factorization are the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\TailCompatibleCauchySectionUp}$ rows. No further carrier, classifier, host-real equality, quotient-stream equality, selector, or ambient completeness scope is exported by the packet.
\end{theorem}
\begin{proof}
Project the carrier tuple of \autoref{def:tail-compatible-cauchy-section-carrier}. Its displayed coordinates first determine the regular-Cauchy family, modulus, precision request, and diagonal indices, and then expose the component rows $W,B,R,D,E$ in the order fixed by \autoref{thm:tail-compatible-cauchy-section-namecert-obligations} and \autoref{thm:tail-compatible-cauchy-section-index-determinacy}.

Read those rows as scope witnesses. The stream window is the $\StreamNameUp$ scope, the budget row is the $\FiniteObservationBudgetSelectorUp$ scope, the readback row is the $\RegSeqRatUp$ scope, the tolerance ledger is the $\DyadicRatCoreUp$ scope, and the seal row is the $\RealUp$ scope. These are the only component rows listed by the carrier surface.

Use \autoref{thm:tail-compatible-cauchy-section-classifier-transport} to transport the classifier along the recorded $\hsame$ support, and use \autoref{thm:tail-compatible-cauchy-section-continuation-replay} to preserve the same ordered route under $\Cont$ replay. The remaining $\Pkg$ and local $\NameCert$ rows only source and name that finite factorization.

Finally, \autoref{thm:tail-compatible-cauchy-section-real-seal-boundary} closes the route at the $\RealUp$ seal. Since the boundary theorem excludes host reals, quotient-stream equality, chosen limits, detached selectors, countable-choice rows, and ambient completeness witnesses, no component scope outside the displayed five can be read from an accepted packet.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section RealUp seal boundary]
\label{thm:tail-compatible-cauchy-section-real-seal-boundary}
Every $\RealUp$-facing consumer read of an accepted $\TailCompatibleCauchySectionUp$ packet factors through the finite route
$$
X,\mu,n,k,i,W,B,R,D,E,H,C,P,N.
$$
The seal coordinate $E$ is reachable only after the shared tail-compatible $\StreamNameUp$ window, $\FiniteObservationBudgetSelectorUp$ budget row, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ ledger have been displayed on the same carrier. The packet exports no host real, quotient stream equality, chosen limit, detached selector, countable-choice row, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:tail-compatible-cauchy-section-namecert-obligations}. It forces every accepted packet to expose the modulus-selected index pair before any readback or seal-facing row is available.

Next read the component surfaces in order. The $\StreamNameUp$ row supplies the finite tail-compatible window, the $\FiniteObservationBudgetSelectorUp$ row admits that window as a finite budgeted request, the $\RegSeqRatUp$ row supplies the selected regular-rational readback, and the $\DyadicRatCoreUp$ row records the tolerance ledger attached to that readback.

Only then can the $\RealUp$ seal row be consumed, and it is preserved solely through the displayed transport, replay, provenance, and local naming rows. Since none of the carrier coordinates is a host real, quotient stream equality, chosen limit, detached selector, countable-choice row, or ambient completeness witness, no Real-facing consumer can obtain such data from the section packet.
\end{proof}

\begin{theorem}[Tail-compatible Cauchy section scoped component readiness]
\label{thm:tail-compatible-cauchy-section-scoped-component-readiness}
Every accepted $\TailCompatibleCauchySectionUp$ section route is scoped by the displayed $\StreamNameUp$ window exposure, $\FiniteObservationBudgetSelectorUp$ budget admission, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, and $\RealUp$ seal, together with the supporting $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert_{\TailCompatibleCauchySectionUp}$ rows. These rows are the whole component scope exported by the packet: they do not expose a host real, quotient stream equality, detached selector, countable-choice row, or ambient completeness witness.
\end{theorem}
\begin{proof}
Start with the NameCert obligations of \autoref{thm:tail-compatible-cauchy-section-namecert-obligations}. They list the carrier admission surface, the two displayed diagonal-section computations, and the ordered component rows from stream window through RealUp seal.

The index-determinacy theorem \autoref{thm:tail-compatible-cauchy-section-index-determinacy} fixes the route selected by the regular-Cauchy family, modulus, and precision request. The component-scope binding theorem \autoref{thm:tail-compatible-cauchy-section-component-scope-binding} then identifies the only component scopes available along that route as $\StreamNameUp$, $\FiniteObservationBudgetSelectorUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$.

Use classifier transport and continuation replay from \autoref{thm:tail-compatible-cauchy-section-classifier-transport} and \autoref{thm:tail-compatible-cauchy-section-continuation-replay} to keep the same rows under $\hsame$ transport and $\Cont$ replay. The $\Pkg$ and local $\NameCert$ rows source and name the same finite factorization rather than adding a further carrier scope.

Finally apply the RealUp seal boundary theorem \autoref{thm:tail-compatible-cauchy-section-real-seal-boundary}. It makes the $\RealUp$ seal the terminal read of the finite route and excludes host reals, quotient-stream equality, detached selectors, countable-choice rows, and ambient completeness witnesses from the exported packet surface.
\end{proof}

\begin{closurestatus}{\TailCompatibleCauchySectionUp}
  \constructivestory{The tail-compatible Cauchy section is generated from a $BHist$ packet that records a Cauchy section, its modulus-selected index pair, finite tail witnesses, and the classifier that checks compatibility with the RealUp seal boundary. The carrier reads the section only through those tail rows; $hsame$ transports the same finite witness data when a history representative changes. Continuation data may extend the section route, but $\Cont$ must preserve the tail-compatible classifier already recorded. The NameCert surface is therefore a composite certificate: it connects a Cauchy section to StreamName, finite observation budget, RegSeqRat, DyadicRatCore, and RealUp through visible tail evidence.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{This chapter binds the tail-compatible Cauchy-section carrier, classifier, index-determinacy row, classifier-transport row, continuation-replay row, NameCert obligations, component scope binding, RealUp seal boundary, and scoped component readiness for the displayed section route.}
  \formalstatus{\axiomCleanV}
  \leanchecked{BEDC.Derived.TailCompatibleCauchySectionUp.taste\_gate}
  \leantarget{BEDC.Derived.TailCompatibleCauchySectionUp.TailCompatibleCauchySectionTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai-composite}
  \notclaimed{It does not claim arbitrary Cauchy section choice, quotient-stream equality, host real equality, or Real equality outside the finite tail-compatible witness route.}
  \upgradepath{Public closure requires an exported consumer surface or bridge evidence for the same StreamName, finite-budget, RegSeqRat, DyadicRatCore, RealUp, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
\end{closurestatus}
