\chapter{A Concrete Naming Certificate for $\FiniteWindowEnvelopeUp$}
\label{ch:concrete-instances-finitewindowenvelope-namecert}
\origin{human}

The $\FiniteWindowEnvelopeUp$ interface is the concrete finite observation boundary for the Real and Completion phase. It packages a selected $\StreamNameUp$ window, its $\DyadicRatCoreUp$ observation ledger, the $\RegSeqRatUp$ seal row that reads the same rational window, and the $\RealUp$ endpoint classifier row that exposes the window to real-number consumers. The envelope is deliberately finite: it certifies exactly the inspected anchor, window, and scale rows, and it exports no diagonal limit, quotient of streams, host real equality, or completeness theorem.

The envelope is the finite-window handoff between \autoref{ch:concrete-instances-streamname-namecert}, \autoref{ch:concrete-instances-dyadicratcore-namecert}, \autoref{ch:concrete-instances-regseqrat-namecert}, and \autoref{ch:concrete-instances-real-namecert}. It consumes a selected $\StreamNameUp$ window, a dyadic observation ledger, a $\RegSeqRatUp$ seal row, and a $\RealUp$ endpoint classifier as one finite package.

\begin{definition}[FiniteWindowEnvelope carrier]
\label{def:finite-window-envelope-carrier}
A $\FiniteWindowEnvelopeUp$ carrier is a finite $\mathsf{BHist}$ package
$$
W=(S,A,B,L,Q,G,E,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $S$ is the $\RatUp$ stream source named by the surrounding $\StreamNameUp$ certificate;
\item $A$ is the selected finite anchor row, recording the inspected source point and the continuation route that reaches it;
\item $B$ is the finite window row, recording the requested length, scale, and local subwindow bounds;
\item $L$ is the $\DyadicRatCoreUp$ observation ledger for every rational read made inside $B$;
\item $Q$ is the $\StreamNameUp$ window classifier row for the same source, anchor, and window;
\item $G$ is the $\RegSeqRatUp$ seal row that reads the dyadic ledger as a regular rational sequence window;
\item $E$ is the $\RealUp$ endpoint classifier row for the same finite window;
\item $P$ is the $\Pkg$ provenance naming the $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RatUp$, and $\NameCert$ source certificates;
\item $N$ is the local $\NameCert_{\FiniteWindowEnvelopeUp}$ provenance row.
\end{enumerate}
The local classifier relates two carriers exactly when their selected finite windows agree by the $\StreamNameUp$ window classifier, their $\DyadicRatCoreUp$ ledgers are equal row by row, their $\RegSeqRatUp$ seal rows classify the same regular rational window, and their $\RealUp$ finite-window endpoint classifiers agree after the displayed $\hsame$ and $\Cont$ transports.
\end{definition}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeTasteGate\_single\_carrier\_alignment}

\begin{theorem}[FiniteWindowEnvelope NameCert obligations]
\label{thm:finite-window-envelope-namecert-obligations}
The local $\NameCert_{\FiniteWindowEnvelopeUp}$ surface consists of five obligations:
\begin{enumerate}
\item carrier formation from the finite $\mathsf{BHist}$ package of \autoref{def:finite-window-envelope-carrier};
\item classifier reflexivity, symmetry, and transitivity for the combined $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ rows;
\item carrier transport under displayed $\hsame$ comparisons and finite window refinement routes;
\item seal handoff from the selected $\StreamNameUp$ window and $\DyadicRatCoreUp$ ledger to the $\RegSeqRatUp$ row;
\item ledger exhaustion for the hidden anchor, selected window, scale, subwindow bound, dyadic readback, and endpoint classifier rows.
\end{enumerate}
\end{theorem}
\begin{proof}
Carrier formation is immediate from the displayed finite package: every coordinate is a visible row, and the package provenance names exactly the certificates that own those rows.

For the classifier laws, apply the component laws already required by the four dependency certificates. Reflexivity uses the same source, anchor, window, dyadic ledger, regular-sequence seal, and endpoint row. Symmetry reverses each displayed classifier row. Transitivity composes the four component comparisons while keeping the anchor and window coordinates synchronized by the common $\StreamNameUp$ row.

Transport under $\hsame$ and $\Cont$ is componentwise. A transported anchor transports its finite window, the dyadic ledger follows the same requested readbacks, and the $\RegSeqRatUp$ and $\RealUp$ rows are repacked against those transported finite reads.

The seal handoff and ledger exhaustion are the remaining two rows. The seal row consumes the same ledger recorded by the carrier, and the exhaustion row says that every finite observation has already appeared as one of the displayed anchor, window, scale, dyadic, regular-sequence, or endpoint coordinates.
\end{proof}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_namecert\_obligations}

\begin{theorem}[FiniteWindowEnvelope RegSeqRat seal handoff]
\label{thm:finite-window-envelope-regseqrat-seal-handoff}
For every accepted $\FiniteWindowEnvelopeUp$ carrier, the $\RegSeqRatUp$ seal row is determined by the selected $\StreamNameUp$ window together with the displayed $\DyadicRatCoreUp$ ledger. If two carriers have the same selected window and equal dyadic ledgers after the displayed transports, then their $\RegSeqRatUp$ seal rows classify the same regular rational finite observation.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-envelope-carrier}. The row $Q$ names the finite $\StreamNameUp$ window, while $L$ records every dyadic rational read performed inside that window.

The $\RegSeqRatUp$ seal row $G$ is attached to those same readbacks. Therefore a second carrier with the same selected window and the same dyadic ledger presents the same regular rational finite observation to the seal interface.

Transport only changes the displayed route used to reach the rows. Since the classifier compares the transported window and ledger before reading the seal row, the $\RegSeqRatUp$ handoff is invariant under the permitted $\hsame$ and $\Cont$ transports.
\end{proof}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff}
\leanvariant{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_regseqrat\_seal\_handoff}

\begin{theorem}[FiniteWindowEnvelope RealUp window exactness]
\label{thm:finite-window-envelope-realup-window-exactness}
For every accepted $\FiniteWindowEnvelopeUp$ carrier, a $\RealUp$ finite-window endpoint read factors through exactly one selected $\StreamNameUp$ window, one $\DyadicRatCoreUp$ observation ledger, and one $\RegSeqRatUp$ seal row. No endpoint read bypasses the carrier by appealing to a host real value, a quotient representative, a diagonal limit, or an ambient completeness theorem.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_realup\_window\_exactness}
\begin{proof}
Begin with a $\RealUp$ endpoint read of the carrier. The endpoint row $E$ is one of the visible coordinates of the source package, so the read first exposes the anchor and finite window rows to which $E$ is attached.

The window row is classified by $Q$, and every rational observation inside it is recorded in $L$. By \autoref{thm:finite-window-envelope-regseqrat-seal-handoff}, the regular rational view of the same finite observation is exactly the seal row $G$.

Thus the endpoint read has no independent source of data. It reaches the $\RealUp$ classifier only through the selected stream window, the dyadic ledger, and the regular-sequence seal, leaving no host value or completion object available to consumers.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope common refinement exactness]
\label{thm:finite-window-envelope-common-refinement-exactness}
Let $W=(S,A,B,L,Q,G,E,P,N)$ and $W'=(S',A',B',L',Q',G',E',P',N')$ be accepted $\FiniteWindowEnvelopeUp$ carriers. If the local classifier relates $W$ and $W'$, then their comparison factors through one displayed selected $\StreamNameUp$ finite window, one transported $\DyadicRatCoreUp$ observation ledger, one $\RegSeqRatUp$ seal row, and one $\RealUp$ endpoint classifier row. Conversely, any such four transported rows, with the package and local certificate provenance already carried by $P,N,P',N'$, repack into the local $\FiniteWindowEnvelopeUp$ classifier.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_common\_refinement\_exactness}
\begin{proof}
For the forward direction, project the carrier tuple of \autoref{def:finite-window-envelope-carrier}. The classifier can inspect only the selected window row $Q$, the dyadic ledger $L$, the seal row $G$, the endpoint row $E$, and their transported counterparts.

Use \autoref{thm:finite-window-envelope-regseqrat-seal-handoff} to identify the transported $\RegSeqRatUp$ seal from the common selected window and the common dyadic ledger. Then use \autoref{thm:finite-window-envelope-realup-window-exactness} to identify the endpoint classifier as the read of that same finite window through the same seal row.

It remains only to rule out hidden comparison data. Apply \autoref{thm:finite-window-envelope-ledger-exhaustion}: every anchor, scale, subwindow, readback, seal, endpoint, package, and certificate row has already appeared in the displayed carrier coordinates.

For the reverse direction, start with the displayed $\StreamNameUp$ window, transported $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, and $\RealUp$ endpoint classifier rows. Repack them with the provenance rows $P,N,P',N'$ into the component order of \autoref{def:finite-window-envelope-carrier}. Since the local classifier is exactly the componentwise comparison of those rows, the two carriers classify together.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope ledger exhaustion]
\label{thm:finite-window-envelope-ledger-exhaustion}
Every accepted $\FiniteWindowEnvelopeUp$ carrier exhausts the hidden finite observation data: the anchor, window length, scale, subwindow bounds, selected offsets, dyadic readbacks, $\RegSeqRatUp$ seal, $\RealUp$ endpoint classifier, $\Pkg$ provenance, and local $\NameCert$ row all occur as displayed coordinates of the carrier or as displayed component rows of those coordinates.
\end{theorem}
\begin{proof}
Inspect the finite package $W$ of \autoref{def:finite-window-envelope-carrier}. The anchor coordinate records the selected source point and its continuation route, while the window coordinate records the length, scale, local bounds, and offsets.

The dyadic ledger coordinate records the rational readbacks. The $\StreamNameUp$ classifier, $\RegSeqRatUp$ seal, and $\RealUp$ endpoint classifier then consume those same rows rather than introducing additional finite observations.

The provenance coordinates $P$ and $N$ account for the package and local naming rows. Since every finite observation field is present in these coordinates or in their displayed component ledgers, the carrier leaves no hidden anchor, window, scale, or endpoint row outside the certificate.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope StreamName RegSeqRat scope]
\label{thm:finite-window-envelope-streamname-regseqrat-scope}
Every accepted $\FiniteWindowEnvelopeUp$ read from a selected finite $\StreamNameUp$ window to a $\RegSeqRatUp$ seal is exhausted by the anchor row, window row, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint classifier, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows displayed in the carrier. The handoff has no additional hidden window selector, rational readback table, endpoint classifier, or completion-side equality field.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-envelope-carrier}. The selected anchor and window rows name the finite $\StreamNameUp$ read, while the dyadic ledger records every rational observation made inside that read.

By \autoref{thm:finite-window-envelope-regseqrat-seal-handoff}, the $\RegSeqRatUp$ seal consumes exactly that selected window and ledger. By \autoref{thm:finite-window-envelope-realup-window-exactness}, the $\RealUp$ endpoint classifier is attached to the same finite window rather than to a separate endpoint object.

The common refinement theorem \autoref{thm:finite-window-envelope-common-refinement-exactness} shows that transported comparisons factor through the same displayed window, ledger, seal, and endpoint rows. Finally, \autoref{thm:finite-window-envelope-ledger-exhaustion} accounts for the anchor, window, scale, subwindow, readback, package, and certificate rows, so the $\StreamNameUp$ to $\RegSeqRatUp$ handoff is scoped by the listed data.
\end{proof}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_streamname\_regseqrat\_scope}

\begin{theorem}[FiniteWindowEnvelope tail projection]
\label{thm:finite-window-envelope-tail-projection}
For every accepted $\FiniteWindowEnvelopeUp$ carrier $W=(S,A,B,L,Q,G,E,P,N)$, any displayed tail read or subwindow read of the accepted envelope factors through the same anchor row $A$, selected $\StreamNameUp$ finite window $Q$, $\DyadicRatCoreUp$ ledger $L$, $\RegSeqRatUp$ seal $G$, $\RealUp$ endpoint classifier $E$, and visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates already listed in the carrier. The projection introduces no quotient stream, diagonal completion, host real equality, or completeness object outside those rows.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:finite-window-envelope-carrier}. The anchor, finite window, dyadic ledger, regular-sequence seal, endpoint classifier, package row, and local naming row are displayed coordinates, and the permitted tail or subwindow read must start from that finite window surface.

Apply \autoref{thm:finite-window-envelope-regseqrat-seal-handoff} to identify the $\RegSeqRatUp$ view of the read with the same selected $\StreamNameUp$ window and $\DyadicRatCoreUp$ ledger. Then use \autoref{thm:finite-window-envelope-common-refinement-exactness} to keep transported comparisons on the same window, ledger, seal, and endpoint rows.

The exhaustion step is \autoref{thm:finite-window-envelope-ledger-exhaustion}, while \autoref{thm:finite-window-envelope-streamname-regseqrat-scope} supplies the non-escape boundary for the stream-to-regular-sequence handoff. Hence every displayed tail or subwindow read is a projection of the listed carrier coordinates.
\end{proof}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_tail\_projection}

\begin{theorem}[FiniteWindowEnvelope tail-projection audit sync]
\label{thm:finite-window-envelope-tail-projection-audit-sync}
Every accepted $\FiniteWindowEnvelopeUp$ carrier assembles its selected finite $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint classifier, displayed $\hsame$ and $\Cont$ transports, $\Pkg$ provenance, and local $\NameCert$ rows into one audit-facing consumer package. Any tail read or subwindow read of the carrier factors through that package, and no such consumer route exports a diagonal limit, quotient stream, host real equality, or completeness object.
\end{theorem}
\begin{proof}
Start with an accepted carrier $W=(S,A,B,L,Q,G,E,P,N)$. The carrier definition exposes the selected finite window $Q$, the dyadic ledger $L$, the seal row $G$, the endpoint row $E$, the package provenance $P$, and the local naming row $N$ as visible coordinates.

The consumer route is assembled by the component exactness results. The handoff theorem \autoref{thm:finite-window-envelope-regseqrat-seal-handoff} identifies the $\RegSeqRatUp$ seal from the selected $\StreamNameUp$ window and the $\DyadicRatCoreUp$ ledger. The endpoint theorem \autoref{thm:finite-window-envelope-realup-window-exactness} ties the $\RealUp$ classifier to the same finite window and seal.

For comparisons between accepted carriers, \autoref{thm:finite-window-envelope-common-refinement-exactness} keeps the transported window, ledger, seal, and endpoint rows on one displayed refinement package. The exhaustion theorem \autoref{thm:finite-window-envelope-ledger-exhaustion} accounts for the anchor, window, scale, subwindow, readback, provenance, and naming rows.

Finally, \autoref{thm:finite-window-envelope-streamname-regseqrat-scope} gives the stream-to-regular-sequence boundary, and \autoref{thm:finite-window-envelope-tail-projection} applies that boundary to tail and subwindow reads. Thus every audit-facing read is a consumer of the same displayed package, with no remaining route to a diagonal limit, quotient stream, host real equality, or completeness object.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope endpoint-source determinacy]
\label{thm:finite-window-envelope-endpoint-source-determinacy}
Let $W=(S,A,B,L,Q,G,E,P,N)$ be an accepted $\FiniteWindowEnvelopeUp$ carrier. Every endpoint read exposed by $W$ has exactly the displayed source chain
$$
(Q,L,G,E)
$$
where $Q$ is the selected $\StreamNameUp$ finite window, $L$ is the $\DyadicRatCoreUp$ observation ledger, $G$ is the $\RegSeqRatUp$ seal row, and $E$ is the $\RealUp$ endpoint classifier row. The read has no second endpoint source outside the listed carrier coordinates and their displayed $\hsame$ and $\Cont$ transports.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeBHistCarrier\_endpoint\_source\_determinacy}
\begin{proof}
Project the carrier of \autoref{def:finite-window-envelope-carrier}. The coordinates $Q,L,G,E$ are the only rows in the package that name a selected window, record its rational observations, seal those observations as a regular rational window, and expose the endpoint classifier.

Apply \autoref{thm:finite-window-envelope-realup-window-exactness} to force every endpoint read through the same selected window, dyadic ledger, and seal row. Apply \autoref{thm:finite-window-envelope-common-refinement-exactness} to keep transported comparisons on those four rows.

Finally, \autoref{thm:finite-window-envelope-ledger-exhaustion} accounts for the anchor, scale, subwindow, readback, package, and local naming data. Since no hidden row remains outside the displayed carrier coordinates, the endpoint source is determined by $(Q,L,G,E)$ together with the displayed transports.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope subwindow refinement closure]
\label{thm:finite-window-envelope-subwindow-refinement-closure}
Let $W=(S,A,B,L,Q,G,E,P,N)$ be an accepted $\FiniteWindowEnvelopeUp$ carrier. Any displayed tail refinement or subwindow refinement of $W$ repacks as the same $\FiniteWindowEnvelopeUp$ surface over the transported anchor row, selected window row, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint classifier, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The repacked surface exports no data beyond those transported rows.
\end{theorem}
\begin{proof}
Begin with a displayed tail or subwindow refinement. By \autoref{thm:finite-window-envelope-tail-projection}, the refinement factors through the anchor, window, ledger, seal, endpoint, transport, package, and naming rows already displayed in $W$.

The stream-to-regular-sequence boundary is fixed by \autoref{thm:finite-window-envelope-streamname-regseqrat-scope}. The endpoint row is fixed by \autoref{thm:finite-window-envelope-endpoint-source-determinacy}, so the refinement cannot choose an independent endpoint source after transport.

Repack the transported rows in the carrier order of \autoref{def:finite-window-envelope-carrier}. The classifier of the repacked envelope is the same componentwise comparison described by the carrier definition, so the transported tail or subwindow read remains closed inside the $\FiniteWindowEnvelopeUp$ surface.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope RegularCauchyName consumer export]
\label{thm:finite-window-envelope-regularcauchyname-consumer-export}
A $\RegularCauchyNameUp$ consumer, or a Real and Completion consumer that reads a $\FiniteWindowEnvelopeUp$ carrier, can read only the consumer package assembled from endpoint-source determinacy, subwindow refinement closure, and the audit-facing tail projection package of \autoref{thm:finite-window-envelope-tail-projection-audit-sync}. Such a consumer obtains the selected $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint row, displayed $\hsame$ and $\Cont$ transports, $\Pkg$ provenance, and $\NameCert$ row, but obtains no diagonal limit, quotient stream, host real equality, selected limit, or completeness object.
\end{theorem}
\begin{proof}
The consumer first receives the audit-facing package of \autoref{thm:finite-window-envelope-tail-projection-audit-sync}. That package already lists the selected finite window, dyadic ledger, regular rational seal, endpoint classifier, transport rows, package provenance, and local naming row.

Endpoint-source determinacy identifies the endpoint reads with the same four source rows $(Q,L,G,E)$. Subwindow refinement closure then shows that every tail or subwindow route repacks inside the same transported envelope surface.

Therefore a $\RegularCauchyNameUp$ consumer, and likewise a Real and Completion consumer, has access exactly to the displayed finite-window package. The excluded objects are not coordinates of the package and are not produced by the cited projection, determinacy, or refinement-closure steps.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope StreamName tail lock]
\label{thm:finite-window-envelope-streamname-tail-lock}
Let $W=(S,A,B,L,Q,G,E,P,N)$ be an accepted $\FiniteWindowEnvelopeUp$ carrier. Every tail read and every subwindow read of the $\mathsf{BHist}$ package remains locked to the selected $\StreamNameUp$ window $Q$, the $\DyadicRatCoreUp$ ledger $L$, the $\RegSeqRatUp$ seal row $G$, the $\RealUp$ endpoint row $E$, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates $P,N$. The read cannot switch to another stream window, another dyadic ledger, another regular rational seal, or a host real endpoint.
\end{theorem}
\begin{proof}
Project the carrier coordinates. The selected window $Q$, ledger $L$, seal $G$, endpoint row $E$, package row $P$, and naming row $N$ are visible rows of the same finite $\mathsf{BHist}$ package.

Apply \autoref{thm:finite-window-envelope-tail-projection} to any tail or subwindow read. It factors the read through the displayed anchor, window, ledger, seal, endpoint, transport, continuation, package, and naming coordinates.

Use \autoref{thm:finite-window-envelope-subwindow-refinement-closure} to repack the transported rows after refinement. Since the repacked surface has the same listed coordinates as its source, the read remains locked to the selected $\StreamNameUp$ window and its associated finite ledger.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope common window lock]
\label{thm:finite-window-envelope-common-window-lock}
Let $W=(S,A,B,L,Q,G,E,P,N)$ and $W'=(S',A',B',L',Q',G',E',P',N')$ be accepted $\FiniteWindowEnvelopeUp$ carriers. Every local classifier comparison between them factors through one common selected finite $\StreamNameUp$ window and one transported $\DyadicRatCoreUp$ ledger, after which the $\RegSeqRatUp$ seal rows, $\RealUp$ endpoint rows, displayed $\hsame$ and $\Cont$ routes, $\Pkg$ provenance, and $\NameCert$ rows are read from that same finite package. No comparison field is supplied by a quotient stream, a diagonal object, or host real equality.
\end{theorem}
\begin{proof}
Start from the local classifier comparison. By \autoref{thm:finite-window-envelope-common-refinement-exactness}, the comparison exposes a single selected window row, a single transported dyadic ledger, one regular-sequence seal row, and one endpoint classifier row.

The seal is determined by \autoref{thm:finite-window-envelope-regseqrat-seal-handoff}. Thus the comparison cannot choose a seal independently of the selected $\StreamNameUp$ window and the transported $\DyadicRatCoreUp$ ledger.

The endpoint side is determined by \autoref{thm:finite-window-envelope-endpoint-source-determinacy}. The exhaustion row \autoref{thm:finite-window-envelope-ledger-exhaustion} then accounts for the transport, continuation, package, and naming rows, leaving no additional comparison source outside the finite carrier.
\end{proof}

\begin{theorem}[FiniteWindowEnvelope Real seal root unblock]
\label{thm:finite-window-envelope-real-seal-root-unblock}
The $\FiniteWindowEnvelopeUp$ carrier supplies the root package needed by downstream Real, $\RegSeqRatUp$, and Completion consumers: an accepted $\mathsf{BHist}$ package binds the selected $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint row, displayed $\hsame$ and $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row into one finite consumer surface. This package exports the exact finite-window endpoint row of \autoref{thm:finite-window-envelope-realup-window-exactness} and the audit-facing tail projection of \autoref{thm:finite-window-envelope-tail-projection-audit-sync}, but exports no quotient stream, host real equality, diagonal limit, or completeness theorem.
\end{theorem}
\begin{proof}
Build the consumer surface from the carrier coordinates. The selected window, dyadic ledger, regular rational seal, endpoint row, transport routes, continuation routes, package provenance, and local naming row are all displayed in the same finite $\mathsf{BHist}$ package.

Use \autoref{thm:finite-window-envelope-realup-window-exactness} to identify the $\RealUp$ endpoint read with the selected $\StreamNameUp$ window, the $\DyadicRatCoreUp$ ledger, and the $\RegSeqRatUp$ seal. This supplies the Real-facing row.

Use \autoref{thm:finite-window-envelope-tail-projection-audit-sync} to expose the same rows to tail and subwindow consumers. The StreamName tail lock and common window lock above keep refinements and comparisons inside the same finite package, so downstream Real, $\RegSeqRatUp$, and Completion consumers receive one root-unblock surface and no external equality or completeness object.
\end{proof}
\leanchecked{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeUp\_StdBridge}

\closureat{FiniteWindowEnvelopeUp}{seedStr}
\closureat{FiniteWindowEnvelopeUp}{obligationStr}
\closureat{FiniteWindowEnvelopeUp}{scopedStr}[BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff]
\closureat{FiniteWindowEnvelopeUp}{publicStr}[BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff]
\closureat{FiniteWindowEnvelopeUp}{bridgedStr}[BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff]
\closureat{FiniteWindowEnvelopeUp}{matureStr}[BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff]

\begin{closurestatus}{\FiniteWindowEnvelopeUp}
  \constructivestory{A $\FiniteWindowEnvelopeUp$ packet is generated from a finite $\StreamNameUp$ window, a $\DyadicRatCoreUp$ ledger, a $\RegSeqRatUp$ seal row, a $\RealUp$ endpoint classifier, displayed transport and continuation rows, package provenance, and local naming.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature theory scope is the standard finite-window envelope interface together with the consumer examples, tail lock, common window lock, and Real seal root-unblock package over the same $\StreamNameUp$ window, $\DyadicRatCoreUp$ ledger, $\RegSeqRatUp$ seal, $\RealUp$ endpoint classifier, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.FiniteWindowEnvelopeUp.FiniteWindowEnvelopeCarrier\_regseqrat\_seal\_handoff}
  \bridgestatus{paperBridge}
  \origin{human}
  \notclaimed{This chapter does not close diagonal limits, quotient streams, host real equality, or completeness.}
  \upgradepath{No further paper-side theory grade remains; formal bridge checking is the remaining upgrade path.}
\end{closurestatus}
