\chapter{A Concrete Naming Certificate for \(\ListUp\)}
\label{ch:concrete-instances-list-namecert}

The list interface \(\ListUp\) is licensed over a source carrier endowed with a \(\NameCert\). The carrier is the inductive sequence built from a nil constructor and a cons constructor consuming one source witness and one shorter list. The classifier is structural sameness lifted from the source classifier: nil-with-nil and cons-with-cons under componentwise sameness. It is not a primitive sequence type; it is licensed only as a derived inductive over the source.

\section{Carrier definition}

\begin{definition}[List carrier]
\label{def:list-carrier}
For a licensed source carrier \(A\), define the inductive list carrier by \(\mathsf{nil}\) and \(\mathsf{cons}(a,\ell)\).
\end{definition}
\leandef{BEDC.Derived.ListUp.ListCarrier}

\section{The certificate}

\begin{definition}[List source specification]
\label{def:list-source-specification}
The source is finite generated sequencing over the source certificate for \(A\).
\end{definition}

\begin{definition}[List pattern specification]
\label{def:list-pattern-specification}
The pattern is nil-or-cons generation with structurally smaller tail.
\end{definition}

\begin{definition}[List classifier specification]
\label{def:list-classifier-specification}
The classifier relates nil with nil and cons with cons when heads are source-classified the same and tails are list-classified the same.
\end{definition}
\leandef{BEDC.Derived.ListUp.ListClassifierSpec}

\begin{theorem}[List classifier is transitive]
\label{thm:list-classifier-transitivity}
For any transitive source classifier on \(A\), the structural list classifier lifted from it is transitive on \(\ListUp(A)\).
\end{theorem}
\begin{proof}
Induct on the first list. Shape mismatches are impossible by the classifier clauses. In the cons-cons-cons case, the head witnesses compose by source transitivity and the tail witnesses compose by the induction hypothesis.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_trans}

\begin{theorem}[History list classifier is transitive]
\label{thm:list-classifier-hsame-trans}
For lists of finite-kernel histories, if the structural list classifier relates \(x\) to \(y\) and \(y\) to \(z\) using \(\hsame\) on heads, then it relates \(x\) to \(z\).
\end{theorem}
\begin{proof}
Induct on the first list. The nil and cons shape mismatches are impossible by the classifier clauses. In the cons-cons-cons case, head witnesses compose by transitivity of \(\hsame\), and the tail witnesses compose by the induction hypothesis.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_trans}

\begin{theorem}[History list classifier is symmetric]
\label{thm:list-classifier-hsame-symm}
For lists of finite-kernel histories, if the structural list classifier relates \(x\) to \(y\) using \(\hsame\) on heads, then it relates \(y\) to \(x\).
\end{theorem}
\begin{proof}
Induct on the first list. Shape mismatches are impossible by the classifier clauses. In the cons-cons case, head witnesses reverse by symmetry of \(\hsame\), and tail witnesses reverse by the induction hypothesis.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_symm}

\begin{lemma}[History list classifier cons inversion]
\label{lem:list-classifier-hsame-cons-inversion}
For BEDC history lists, if the structural classifier relates \(x::xs\) to
\(y::ys\) using \(\hsame\), then \(x\) is internally the same history as \(y\)
and the tails \(xs\) and \(ys\) are structurally classified by \(\hsame\).
\end{lemma}
\begin{proof}
Eliminate the cons-cons classifier witness. Its head component is the
\(\hsame(x,y)\) witness, and its tail component is the structural classifier
witness for \(xs\) and \(ys\).
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_cons\_inversion}

\begin{theorem}[History list classifier singleton equivalence]
\label{thm:list-classifier-hsame-singleton-iff}
For BEDC history singleton lists, structural classification by \(\hsame\) is
equivalent to \(\hsame\) of the two displayed histories.
\end{theorem}
\begin{proof}
Unfold the singleton cons-cons classifier shape. The forward direction keeps
the head \(\hsame\) witness; the reverse direction pairs that head witness with
the nil-tail classifier clause.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_singleton\_iff}

\begin{theorem}[History list classifier head transport]
\label{thm:list-classifier-hsame-cons-head-transport}
For BEDC history lists, if \(y\) is internally the same history as \(z\) and
the structural classifier relates \(x::xs\) to \(y::ys\), then the structural
classifier also relates \(x::xs\) to \(z::ys\).
\end{theorem}
\begin{proof}
Eliminate the cons-cons classifier witness. Compose its head witness
\(\hsame(x,y)\) with the replacement witness \(\hsame(y,z)\), and keep the
tail classifier witness unchanged.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_cons\_head\_transport}

\begin{theorem}[History list classifier is stable under $e0$-mapping]
\label{thm:list-classifier-hsame-map-e0}
For BEDC history lists, structural classification by $\hsame$ is preserved when every entry of both lists is mapped through the $e0$ history constructor.
\end{theorem}
\begin{proof}
Induct on the first list. Nil and cons shape mismatches are impossible by the classifier clauses. In the cons-cons case, apply $e0$-congruence of $\hsame$ to the heads and apply the induction hypothesis to the classified tails.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_map\_e0}

\begin{theorem}[History list classifier reflects $e0$-mapping]
\label{thm:list-classifier-hsame-map-e0-inversion}
For BEDC history lists, if the lists obtained by mapping every entry through
the $e0$ history constructor are structurally classified by $\hsame$, then the
original lists are structurally classified by $\hsame$.
\end{theorem}
\begin{proof}
Induct on the first list. Nil and cons shape mismatches are impossible by the
classifier clauses. In the cons-cons case, invert the mapped head witness using
the $e0$ constructor characterization for $\hsame$, then apply the induction
hypothesis to the mapped-tail classifier witness.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_map\_e0\_inversion}

\begin{theorem}[History list classifier is stable under $e1$-mapping]
\label{thm:list-classifier-hsame-map-e1}
For BEDC history lists, structural classification by $\hsame$ is preserved when every entry of both lists is mapped through the $e1$ history constructor.
\end{theorem}
\begin{proof}
Induct on the first list. Nil and cons shape mismatches are impossible by the classifier clauses. In the cons-cons case, apply $e1$-congruence of $\hsame$ to the heads and apply the induction hypothesis to the classified tails.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_map\_e1}

\begin{theorem}[History list classifier reflects $e1$-mapping]
\label{thm:list-classifier-hsame-map-e1-inversion}
For BEDC history lists, if the lists obtained by mapping every entry through
the $e1$ history constructor are structurally classified by $\hsame$, then the
original lists are structurally classified by $\hsame$.
\end{theorem}
\begin{proof}
Induct on the first list. Nil and cons shape mismatches are impossible by the
classifier clauses. In the cons-cons case, invert the mapped head witness using
the $e1$ constructor characterization for $\hsame$, then apply the induction
hypothesis to the mapped-tail classifier witness.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_map\_e1\_inversion}

\begin{theorem}[History list classifier separates mixed mapped tags]
\label{thm:list-classifier-mixed-tag-empty}
For BEDC history lists, if the list obtained by mapping every entry of \(x\)
through \(e0\) is structurally classified by \(\hsame\) with the list obtained
by mapping every entry of \(y\) through \(e1\), then \(x\) and \(y\) are both
empty.
\end{theorem}
\begin{proof}
Split both lists by constructors. The nil-nil case is immediate. Nil-cons and
cons-nil cases contradict the structural classifier clauses. In the cons-cons
case, the head witness would relate an \(e0\)-tagged history to an \(e1\)-tagged
history, contradicting BEDC history constructor separation.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_map\_e0\_map\_e1\_empty}

\begin{theorem}[History list classifier preserves length]
\label{thm:list-classifier-hsame-length-eq}
For lists of finite-kernel histories, structural classification by \(\hsame\) can only relate lists with equal length.
\end{theorem}
\begin{proof}
Induct on the first list. Nil can only classify with nil. In the cons case, classifier inversion forces the second list to be cons, and the induction hypothesis gives equality of the tail lengths.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_length\_eq}

\begin{definition}[List stability certificate]
\label{def:list-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item reflexivity by list induction
  \item transitivity by paired source/list induction
  \item nil/cons separation
  \item closure under cons
  \item tail inversion and head inversion for classified cons values
\end{enumerate}
\end{definition}
\leanchecked{BEDC.Derived.ListUp.listClassifier\_refl}

\begin{theorem}[List classifier stability under append]
\label{thm:list-classifier-append-hsame}
For BEDC histories, if two list pairs are structurally classified by \(\HSame\),
then appending the first components and appending the second components
preserves structural classification.
\end{theorem}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_append\_hsame}

\begin{proof}
Induct on the first list. The empty case returns the classification of the
second pair. In the cons case, invert the second list and the structural
classifier; the head \(\HSame\) witness is reused and the tail follows from
the induction hypothesis.
\end{proof}

\begin{theorem}[History list classifier left append cancellation]
\label{thm:list-classifier-hsame-append-left-cancel}
For BEDC history lists, structural classification of \(p{++}x\) with
\(p{++}y\) using \(\hsame\) on heads determines structural classification of
\(x\) with \(y\).
\end{theorem}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_append\_left\_cancel}

\begin{proof}
Induct on the common prefix \(p\). The empty-prefix case is the given
classification. In the cons-prefix case, invert the structural classifier and
apply the induction hypothesis to the classified tails.
\end{proof}

\begin{theorem}[Classified list prefix cancellation]
\label{thm:list-classifier-hsame-append-left-cancel-classified}
For BEDC history lists, if \(p\) and \(p'\) are structurally classified by
\(\hsame\), and \(p{++}x\) is structurally classified with \(p'{++}y\), then
\(x\) is structurally classified with \(y\).
\end{theorem}
\begin{proof}
Induct on \(p\). The empty case forces \(p'\) to be empty by the prefix
classifier, leaving the appended classifier. In the cons case, the prefix
classifier and appended classifier both expose matching classified tails, and
the induction hypothesis applies to those tails.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_hsame\_append\_left\_cancel\_classified}

\begin{theorem}[List classifier stability under reverse]
\label{thm:list-classifier-reverse-hsame}
For BEDC history lists, structural classification by $\HSame$ is preserved when both lists are reversed.
\end{theorem}
\begin{proof}
Induct on the first list. Shape mismatches are impossible by the classifier clauses. In the cons-cons case, reverse turns each list into the reversed tail followed by a singleton head; the induction hypothesis handles the tails and append stability combines it with the head witness.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_reverse\_hsame}

\begin{theorem}[List classifier reverse inversion]
\label{thm:list-classifier-reverse-hsame-inversion}
For BEDC history lists, if the reversed lists are structurally classified by
\(\HSame\), then the original lists are structurally classified by \(\HSame\).
\end{theorem}
\begin{proof}
Apply reverse stability to the classified reversed lists. The double reverse of
each list is definitionally identified with the original list by list
reverse-reverse induction, giving the desired structural classifier.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_reverse\_hsame\_inversion}

\begin{theorem}[List classifier append right cancellation]
\label{thm:list-classifier-append-right-cancel-hsame}
For BEDC history lists, if adding the same right suffix to two lists gives a
structural \(\HSame\)-classification, then the original lists are structurally
classified.
\end{theorem}
\begin{proof}
Reverse the classified append witnesses. The common right suffix becomes a
common left prefix, so left-append cancellation removes it. Reversing the
remaining classifier witness returns the original list order.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_append\_right\_cancel\_hsame}

\begin{theorem}[List classifier right cancellation with equivalent suffixes]
\label{thm:list-classifier-append-right-cancel-with-hsame-suffix}
For BEDC history lists, if two right suffixes are structurally classified by
\(\HSame\), and appending those suffixes to \(x\) and \(y\) gives a structural
\(\HSame\)-classification, then \(x\) and \(y\) are structurally classified.
\end{theorem}
\begin{proof}
Use symmetry on the suffix classifier and append stability with reflexivity on
the left list \(y\) to classify \(y{++}\mathit{suffix}'\) with
\(y{++}\mathit{suffix}\). Transitivity aligns the appended classification to a
common right suffix, and ordinary right-append cancellation removes it.
\end{proof}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_append\_right\_cancel\_with\_hsame\_suffix}

\begin{theorem}[List classifier transitivity from a source certificate]
\label{thm:list-classifier-trans-from-namecert}
If the source classifier is supplied by a \(\NameCert\), then the lifted list classifier is transitive on finite list spines.
\end{theorem}
\leanchecked{BEDC.Derived.ListUp.ListClassifierSpec\_trans\_from\_nameCert}

\begin{proof}
Proceed by induction on the first list. The nil case forces the middle list to be nil, then the final list is nil. In the cons case, nil/cons mismatches are impossible by classifier inversion. For matching cons constructors, transitivity of the source certificate handles the heads and the induction hypothesis handles the tails.
\end{proof}

\begin{definition}[List ledger policy]
\label{def:list-ledger-policy}
Record the finite constructor spine and the source ledger for each element.
\end{definition}

\begin{theorem}[Concrete $\ListUp$ naming certificate]
\label{thm:concrete-list-namecert}
Assume a source carrier $A$ is equipped with a $\NameCert$ for the source classifier $\sim_A$. Let $\ListUp(A)$ be the generated list carrier with nil and cons constructors, and let $\mathsf{ListClassifierSpec}(\sim_A)$ be the lifted structural classifier. Then the generated carrier, lifted classifier, and inherited transport data satisfy the naming-certificate obligations for $\ListUp(A)$.
\end{theorem}
\begin{proof}
The nil constructor supplies an inhabited carrier. Classifier reflexivity is by induction on the generated list spine, using the reflexivity field of the source certificate at each cons head. Symmetry is by induction on the structural classifier derivation: nil is immediate, and the cons-cons case uses source symmetry on the heads and the induction hypothesis on the tails. Transitivity is the structural induction of Theorem~\ref{thm:list-classifier-trans-from-namecert}, using the source certificate transitivity field for matching heads. Carrier transport follows by induction over the lifted classifier derivation, with nil transported to nil and cons transported componentwise by the source certificate field and the tail induction hypothesis.
\end{proof}

\begin{corollary}[\(\ListUp\) is licensed, not primitive]
\label{cor:list-licensed-not-primitive}
\(\ListUp\) is licensed as a finite inductive sequence over \(A\).
\end{corollary}
