\chapter{A Concrete Naming Certificate for $\SelectedTailSeedUp$}
\label{ch:concrete-instances-selected-tail-seed-namecert}
\origin{ai}

The $\SelectedTailSeedUp$ packet realizes the stationary selected-tail seed exactness surface of \autoref{ch:visions-real-completeness} as a finite concrete NameCert carrier. It is structurally composite over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\FiniteTailFilterUp$: rational endpoints are read through \autoref{ch:concrete-instances-rat-namecert}; stream windows through \autoref{ch:concrete-instances-streamname-namecert}; regular-rational readback through \autoref{ch:concrete-instances-regseqrat-namecert}; dyadic tolerance ledgers through \autoref{ch:concrete-instances-dyadicratcore-namecert}; Real sealing through \autoref{ch:concrete-instances-real-namecert}; and selected finite-tail filtering through \autoref{ch:concrete-instances-finite-tail-filter-namecert}. The packet supplies the finite handoff used by \autoref{thm:real-completeness-stationary-rational-selected-tail-seed-exactness} without quotient streams, host real equality, or ambient completeness.

\begin{definition}[Selected-tail seed carrier]
\label{def:selected-tail-seed-carrier}
A $\SelectedTailSeedUp$ carrier is a finite $\BHist$ packet
$$
T=(Q,E,A,W,K,S,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the $\RatUp$ seed-rational row naming the stationary rational endpoint.
\item $E$ is the endpoint-exactness row comparing the selected seed endpoint with the rational seed under the displayed rational classifier.
\item $A$ is the admission row for the selected finite tail, read against $\FiniteTailFilterUp$.
\item $W$ is the $\StreamNameUp$ window exposing the selected stationary tail segment.
\item $K$ is the $\RegSeqRatUp$ readback row for the stationary regular-rational sequence at the selected window.
\item $S$ is the $\DyadicRatCoreUp$ tolerance and arithmetic ledger attached to the selected endpoint.
\item $R$ is the $\RealUp$ seal row obtained from the selected stationary readback.
\item $H$ records componentwise $\hsame$ transport for $Q,E,A,W,K,S,R,P,N$.
\item $C$ records displayed $\Cont$ replay from rational seed through selected finite tail, stream window, regular-rational readback, dyadic ledger, and Real seal.
\item $P$ is the $\Pkg$ provenance over $\SelectedTailSeedUp$, $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\FiniteTailFilterUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\SelectedTailSeedUp}$ row.
\end{enumerate}
The carrier exports no quotient stream, host real equality, countable-choice selector, detached limit object, or ambient Real-completeness coordinate.
\end{definition}

\begin{theorem}[Selected-tail seed NameCert obligations]
\label{thm:selected-tail-seed-namecert-obligations}
For the carrier of \autoref{def:selected-tail-seed-carrier}, the local $\NameCert_{\SelectedTailSeedUp}$ surface consists exactly of carrier admission for $T=(Q,E,A,W,K,S,R,H,C,P,N)$, rational seed admission through $Q$, endpoint exactness through $E$, finite-tail admission through $A$, stationary stream-window exposure through $W$, regular-rational readback through $K$, dyadic tolerance and arithmetic exposure through $S$, Real sealing through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier. Its coordinates list the rational seed, endpoint-exactness row, finite-tail admission row, selected stream window, regular-rational readback, dyadic ledger, Real seal, transport, replay, provenance, and local name.

The sibling certificate surfaces account for the data-bearing rows. $\RatUp$ supplies $Q$; $\FiniteTailFilterUp$ supplies $A$; $\StreamNameUp$ supplies $W$; $\RegSeqRatUp$ supplies $K$; $\DyadicRatCoreUp$ supplies $S$; and $\RealUp$ supplies $R$.

The endpoint row $E$ is therefore not an additional host equality. It is the displayed comparison tying the selected finite tail back to the stationary rational seed, while $H,C,P,N$ only transport, replay, source, and name the already displayed rows. These rows exhaust the local NameCert obligations.
\end{proof}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Selected-tail seed Real-window handoff]
\label{thm:selected-tail-seed-real-window-handoff}
Every Real-window consumer of an accepted $\SelectedTailSeedUp$ packet factors through the finite route
$$
Q,E,A,W,K,S,R,H,C,P,N.
$$
In particular, the stationary rational selected finite-window endpoint is read as a finite $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ handoff rather than as quotient stream equality or host real equality.
\end{theorem}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedCarrier\_real\_window\_handoff}
\begin{proof}
Start with the selected finite-tail admission row $A$. It identifies the tail segment whose stationary window is visible, but it does not by itself expose a Real-facing endpoint.

Next read the route through $W,K,S$. The stream window displays the selected stationary segment, the regular-rational row reads that segment as a regular sequence observation, and the dyadic ledger records the finite tolerance and arithmetic used by the endpoint exactness row.

Finally pass through $R,H,C,P,N$. The Real seal $R$ is downstream of the selected finite route, and the structural rows only preserve the displayed handoff. Since the carrier has no quotient stream, host real equality, countable-choice selector, detached limit, or ambient completeness coordinate, every Real-window consumer remains inside the finite route.
\end{proof}

\begin{theorem}[Selected-tail finite-tail admission exactness]
\label{thm:selected-tail-seed-finite-tail-admission-exactness}
For every accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, the admission row $A$ is the unique displayed gate through which the selected stationary tail can be read before any $\StreamNameUp$ window or $\RegSeqRatUp$ readback is consumed. Thus every use of $W$ or $K$ in a $\SelectedTailSeedUp$ consumer first factors through the $\FiniteTailFilterUp$ admission witnessed by $A$.
\end{theorem}
\begin{proof}
Project the accepted carrier to its displayed rows. The row $A$ is the only coordinate whose type names selected finite-tail admission; the later rows $W$ and $K$ name a stream window and a regular-rational readback, but neither row carries the finite-tail classifier by itself.

The constructive factorization is therefore obtained by ordering the projections. A consumer asking for $W$ or $K$ first reads $A$, obtaining the $\FiniteTailFilterUp$-admitted selected tail segment, and then passes the admitted segment to the $\StreamNameUp$ window row and the $\RegSeqRatUp$ readback row.

No omitted coordinate can bypass this order. The carrier exports no quotient stream, detached limit object, countable-choice selector, or host real equality, so there is no second admission path from a raw tail to $W$ or $K$ outside the displayed finite-tail row.
\end{proof}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedCarrier\_finite\_tail\_admission\_exactness}

\begin{theorem}[Selected-tail endpoint exactness readback stability]
\label{thm:selected-tail-seed-endpoint-exactness-readback-stability}
For an accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the endpoint exactness row $E$ is stable under $\hsame$ transport and displayed $\Cont$ replay only as part of the full readback surface $Q,E,A,W,K,S,H,C,P,N$. In particular, $E$ cannot be replayed as an isolated host equality detached from the rational seed $Q$, the window and readback rows $W,K$, the dyadic ledger $S$, and the transport, replay, provenance, and naming rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with the comparison encoded by $E$. It relates the selected seed endpoint to the rational seed, so the row already depends on $Q$ before any stability claim can be read.

The readback side is then supplied by $W,K,S$. The stream row displays the selected stationary window, the regular-rational row reads that window, and the dyadic ledger records the finite tolerance and arithmetic against which endpoint exactness is checked.

Stability is the final structural step. The row $H$ transports the displayed coordinates componentwise by $\hsame$, the row $C$ replays the displayed construction by $\Cont$, and the rows $P,N$ keep the replay sourced and named inside the local $\NameCert_{\SelectedTailSeedUp}$ packet. Since none of these rows exports a host equality coordinate, the stable endpoint exactness is exactly the displayed finite readback surface.
\end{proof}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedCarrier\_endpoint\_exactness\_readback\_stability}

\begin{theorem}[Selected-tail Real-seal nonescape obligation]
\label{thm:selected-tail-seed-real-seal-nonescape-obligation}
For an accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the Real seal row $R$ can be consumed only after the $\RatUp$, $\FiniteTailFilterUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ rows $Q,A,W,K,S$ have been displayed, with endpoint exactness supplied by $E$ and structural replay supplied by $H,C,P,N$. Consequently a $\SelectedTailSeedUp$ Real-window consumer has no route through quotient streams, host real equality, countable choice, detached limits, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the Real-facing row $R$. By the carrier definition, $R$ is obtained from the selected stationary readback, so it sits downstream of the rational seed, finite-tail admission, stream window, regular-rational readback, and dyadic tolerance ledger.

The nonescape route is the displayed composition $Q,A,W,K,S,E,R,H,C,P,N$. The rows $Q,A,W,K,S$ expose the finite data needed for the Real seal, $E$ ties the selected endpoint to the rational seed, and $H,C,P,N$ preserve, replay, source, and name the constructed route.

The exclusions are therefore structural, not analytic. Quotient streams, host real equality, countable choice, detached limits, and ambient Real completeness are not coordinates of $T$, and a consumer of $R$ can only project and compose the rows that the finite $\NameCert_{\SelectedTailSeedUp}$ carrier displays.
\end{proof}

\begin{theorem}[Selected-tail seed Real-seal handoff]
\label{thm:selected-tail-seed-real-seal-handoff}
For an accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, every access to the $\RealUp$ seal row $R$ factors through the finite route
$$
Q,E,A,W,K,S,H,C,P,N.
$$
Thus the selected stationary endpoint reaches the Real seal only through the displayed rational seed, endpoint exactness, finite-tail admission, stream window, regular-rational readback, dyadic ledger, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert_{\SelectedTailSeedUp}$ naming, with no quotient stream or ambient-completeness coordinate.
\end{theorem}
\begin{proof}
Use the carrier displayed in \autoref{def:selected-tail-seed-carrier}. Its rows place $R$ downstream of $Q,E,A,W,K,S$, while $H,C,P,N$ are the structural rows that transport, replay, source, and name the same finite data.

The local obligation theorem \autoref{thm:selected-tail-seed-namecert-obligations} identifies these rows as the whole $\NameCert_{\SelectedTailSeedUp}$ surface. The Real-window handoff theorem \autoref{thm:selected-tail-seed-real-window-handoff} then gives the consumer route through the same finite packet.

The sibling chapters named in the introduction supply the row meanings: $\RatUp$ for $Q$, $\FiniteTailFilterUp$ for $A$, $\StreamNameUp$ for $W$, $\RegSeqRatUp$ for $K$, $\DyadicRatCoreUp$ for $S$, and $\RealUp$ for $R$. Since quotient streams and ambient completeness are not coordinates of $T$, the Real seal has no other entry path.
\end{proof}

\begin{theorem}[Selected-tail seed classifier transport]
\label{thm:selected-tail-seed-classifier-transport}
For accepted carriers $T=(Q,E,A,W,K,S,R,H,C,P,N)$ and $T'=(Q',E',A',W',K',S',R',H',C',P',N')$ of \autoref{def:selected-tail-seed-carrier}, componentwise $\hsame$ transport of $Q,E,A,W,K,S,R,H,C,P,N$ to $Q',E',A',W',K',S',R',H',C',P',N'$ preserves the selected-tail classifier exactly as a displayed $\SelectedTailSeedUp$ classifier. It does not collapse endpoint exactness $E$ into host equality of Real endpoints or erase the finite-tail, stream-window, regular-rational, and dyadic rows needed to read the classifier.
\end{theorem}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedCarrier\_classifier\_transport}
\begin{proof}
Read the transport row $H$ in the carrier of \autoref{def:selected-tail-seed-carrier}. It is componentwise transport for the displayed rows, so each selected-tail coordinate is carried with its own classifier role rather than through a single host equality.

The obligations in \autoref{thm:selected-tail-seed-namecert-obligations} show which classifier pieces must remain visible: rational seed admission, endpoint exactness, finite-tail admission, stream-window exposure, regular-rational readback, dyadic ledger, Real seal, replay, provenance, and naming. Transport that preserves the $\NameCert_{\SelectedTailSeedUp}$ surface must therefore preserve all these rows.

Finally apply the Real-window handoff of \autoref{thm:selected-tail-seed-real-window-handoff}. Because every Real-facing consumer still passes through $Q,E,A,W,K,S,R,H,C,P,N$, endpoint exactness cannot be reinterpreted as host Real equality, and classifier transport remains a finite selected-tail transport.
\end{proof}

\begin{theorem}[Selected-tail seed window readback coherence]
\label{thm:selected-tail-seed-window-readback-coherence}
For every accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, the stream window $W$, regular-rational readback $K$, dyadic ledger $S$, and Real seal $R$ form one coherent finite readback chain inside the $\SelectedTailSeedUp$ packet. Any consumer of $R$ must read $W$ through $K$ and $S$, while $H,C,P,N$ preserve, replay, source, and name that same chain.
\end{theorem}
\leanchecked{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedWindowReadbackCoherence}
\begin{proof}
Begin with $W$. The introduction grounds $W$ in $\StreamNameUp$, and \autoref{def:selected-tail-seed-carrier} makes it the selected stationary tail window rather than a quotient stream.

Next read $K$ and $S$. The $\RegSeqRatUp$ row $K$ reads the selected window as regular-rational data, and the $\DyadicRatCoreUp$ row $S$ records the finite tolerance and arithmetic ledger for that readback.

The Real row $R$ is then the seal obtained from this selected stationary readback. By \autoref{thm:selected-tail-seed-namecert-obligations} these rows are part of the same local NameCert surface, and by \autoref{thm:selected-tail-seed-real-window-handoff} every Real-window consumer remains on the finite route. The structural rows $H,C,P,N$ do not create a second readback; they preserve the single chain.
\end{proof}

\begin{theorem}[Selected-tail seed tail-window determinacy]
\label{thm:selected-tail-seed-tail-window-determinacy}
For every accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, any consumer route that exposes the selected stationary endpoint as a $\RealUp$ seal from the same finite-tail admission row $A$ must use the displayed chain $A,W,K,S,R$, with endpoint exactness supplied by $E$ and structural rows supplied by $H,C,P,N$. No alternate stream window, regular-rational readback, dyadic ledger, or Real seal is a $\SelectedTailSeedUp$ consumer route unless it is supplied as one of these carrier rows.
\end{theorem}
\begin{proof}
Project the carrier $T$. The finite-tail admission row is the displayed coordinate $A$, and \autoref{thm:selected-tail-seed-finite-tail-admission-exactness} makes the selected endpoint pass through that finite admission gate with endpoint exactness $E$.

Next apply \autoref{thm:selected-tail-seed-window-readback-coherence}. Once $A$ is fixed, the consumer-visible readback is the single window chain $W,K,S,R$: $W$ exposes the selected stream window, $K$ reads it as regular-rational data, $S$ records the dyadic ledger, and $R$ seals the same selected stationary endpoint as a Real row.

Finally apply \autoref{thm:selected-tail-seed-real-seal-handoff}. The structural rows $H,C,P,N$ preserve, replay, source, and name the displayed chain, while quotient streams, host real equality, detached limits, and ambient Real completeness are not coordinates of the carrier. Hence a route using a different window, readback, ledger, or seal is not a $\SelectedTailSeedUp$ consumer route unless that data has already been supplied as one of the rows of $T$.
\end{proof}

\begin{theorem}[Selected-tail seed stationary-endpoint coverage]
\label{thm:selected-tail-seed-stationary-endpoint-coverage}
For every accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, the stationary selected endpoint is exposed only through the finite route
$$
Q,E,A,W,K,S
$$
before the Real seal row $R$ is consumed. These rows are sufficient for the local selected-tail endpoint read used by Real-window consumers: $Q$ supplies the rational seed, $E$ supplies endpoint exactness, $A$ admits the selected finite tail, $W$ exposes the stationary window, $K$ reads that window as regular-rational data, and $S$ records the dyadic tolerance ledger.
\end{theorem}
\begin{proof}
Project the carrier and apply \autoref{thm:selected-tail-seed-namecert-obligations}. The displayed NameCert surface contains exactly the seed, exactness, finite-tail admission, stream-window, regular-rational, dyadic-ledger, and Real-seal rows together with the structural rows.

The local endpoint read begins before the Real seal. By \autoref{thm:selected-tail-seed-finite-tail-admission-exactness}, the selected stationary tail must first pass through $A$ before any use of $W$ or $K$.

Finally apply \autoref{thm:selected-tail-seed-window-readback-coherence}. The window-readback chain is $W,K,S,R$, so the endpoint visible to Real-window consumers has already been routed through $Q,E,A,W,K,S$ before the seal row $R$ is read.
\end{proof}

\begin{theorem}[Selected-tail seed dyadic-ledger readback coverage]
\label{thm:selected-tail-seed-dyadic-ledger-readback-coverage}
For every accepted carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$ of \autoref{def:selected-tail-seed-carrier}, the row $S$ is the unique displayed dyadic tolerance and arithmetic ledger mediating the regular-rational readback $K$ and the Real seal $R$. No $\SelectedTailSeedUp$ consumer may pass from $W,K$ to $R$ while omitting $S$.
\end{theorem}
\begin{proof}
Project $T$ to its displayed rows. The carrier definition names $S$ as the only $\DyadicRatCoreUp$ tolerance and arithmetic ledger attached to the selected endpoint, while $K$ is the regular-rational readback row and $R$ is the Real seal row.

Apply \autoref{thm:selected-tail-seed-namecert-obligations}. The local NameCert surface lists $K$, $S$, and $R$ as separate required obligations, so the dyadic ledger cannot be absorbed into either the readback row or the Real seal.

The Real-facing route is fixed by \autoref{thm:selected-tail-seed-real-seal-nonescape-obligation} and \autoref{thm:selected-tail-seed-real-seal-handoff}. Both routes pass through $S$ before consuming $R$, and the carrier exports no alternate coordinate that could mediate the same transition.
\end{proof}

\begin{theorem}[Selected-tail seed Real-completion boundary]
\label{thm:selected-tail-seed-real-completion-boundary}
Every accepted $\SelectedTailSeedUp$ carrier supplies a finite handoff into Real-window consumers, but it does not assert Real completeness, quotient-stream equality, countable-choice selection, detached limits, or host real equality. Any consumer that needs one of those completion-facing boundaries must obtain it from a separate L10 chapter rather than from the local rows $Q,E,A,W,K,S,R,H,C,P,N$.
\end{theorem}
\begin{proof}
First use \autoref{thm:selected-tail-seed-stationary-endpoint-coverage}. The stationary endpoint exposed by the packet is the finite route $Q,E,A,W,K,S$ before the Real seal row is read.

Next use \autoref{thm:selected-tail-seed-dyadic-ledger-readback-coverage}. The passage from regular-rational readback to Real seal must include the displayed dyadic ledger $S$, so the packet supplies a concrete finite handoff rather than an ambient completion principle.

Finally combine \autoref{thm:selected-tail-seed-real-window-handoff} with \autoref{thm:selected-tail-seed-real-seal-handoff}. Both the consumer route and the seal route remain inside the listed carrier rows, whose definition explicitly exports no quotient stream, host real equality, countable-choice selector, detached limit object, or ambient Real-completeness coordinate.
\end{proof}

\begin{theorem}[Selected-tail rational seed admission]
\label{thm:selected-tail-seed-rational-seed-admission}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the rows $Q$ and $E$ are the only rational seed and endpoint-exactness admission rows in the local packet. The rational seed enters through $Q$, endpoint exactness is witnessed through $E$, and neither role may be replaced by host $\RealUp$ equality or by a detached completion-facing comparison.
\end{theorem}
\begin{proof}
Project the accepted carrier. By \autoref{def:selected-tail-seed-carrier}, $Q$ is the unique displayed $\RatUp$ seed-rational row, and $E$ is the displayed endpoint-exactness row comparing the selected seed endpoint with that rational seed.

Apply \autoref{thm:selected-tail-seed-namecert-obligations}. The local $\NameCert_{\SelectedTailSeedUp}$ surface lists rational seed admission through $Q$ and endpoint exactness through $E$ as separate obligations, while the other rows serve finite-tail admission, stream readback, dyadic accounting, Real sealing, transport, replay, provenance, and naming.

Finally use \autoref{thm:selected-tail-seed-real-completion-boundary}. The packet does not export host real equality, quotient streams, detached limits, countable-choice selection, or ambient Real completeness, so no completion-facing equality can replace the displayed $Q,E$ admission plane.
\end{proof}

\begin{theorem}[Selected-tail stream--regular--dyadic compatibility]
\label{thm:selected-tail-seed-stream-regseq-dyadic-compatibility}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the rows $W,K,S$ form the unique displayed compatibility chain from $\StreamNameUp$ through $\RegSeqRatUp$ to $\DyadicRatCoreUp$ before the Real seal row $R$ is consumed. Thus a Real-window consumer cannot read $R$ without first passing through the stream window, regular-rational readback, and dyadic ledger displayed by $W,K,S$.
\end{theorem}
\begin{proof}
Start with the readback chain. \autoref{thm:selected-tail-seed-window-readback-coherence} identifies $W,K,S,R$ as one coherent finite readback chain inside the accepted packet.

The dyadic step is not optional. By \autoref{thm:selected-tail-seed-dyadic-ledger-readback-coverage}, the row $S$ is the unique displayed dyadic tolerance and arithmetic ledger mediating the regular-rational readback $K$ and the Real seal $R$.

The Real-facing boundary then fixes the order of consumption. \autoref{thm:selected-tail-seed-real-seal-handoff} and \autoref{thm:selected-tail-seed-real-completion-boundary} keep the consumer route inside the finite carrier rows, so the path to $R$ is exactly the displayed $\StreamNameUp \to \RegSeqRatUp \to \DyadicRatCoreUp$ compatibility chain $W,K,S$.
\end{proof}

\begin{theorem}[Selected-tail package provenance exactness]
\label{thm:selected-tail-seed-pkg-provenance-exactness}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the rows $P$ and $N$ name exactly the finite route
$$
Q,E,A,W,K,S,R,H,C.
$$
They cannot add quotient streams, countable-choice selectors, detached limits, ambient completeness, or host equality beyond the displayed selected-tail seed packet.
\end{theorem}
\begin{proof}
Inventory the carrier rows. The data-bearing route is $Q,E,A,W,K,S,R$, and the structural route is $H,C$; by \autoref{def:selected-tail-seed-carrier}, $P$ is the $\Pkg$ provenance over these displayed ingredients and $N$ is the local $\NameCert_{\SelectedTailSeedUp}$ row.

Apply \autoref{thm:selected-tail-seed-namecert-obligations}. The provenance and naming rows source and name the existing route; they are not independent coordinates carrying analytic completion data.

Finally apply \autoref{thm:selected-tail-seed-real-completion-boundary}. Since the packet exports no quotient stream, host real equality, countable-choice selector, detached limit object, or ambient Real-completeness coordinate, $P,N$ preserve provenance exactly for $Q,E,A,W,K,S,R,H,C$ and cannot enlarge the route.
\end{proof}

\begin{theorem}[Selected-tail seed dependency readiness triad]
\label{thm:selected-tail-seed-dependency-readiness-triad}
Every accepted $\SelectedTailSeedUp$ carrier displays a root-ready dependency triad. The rational endpoint plane is $Q,E$; the finite-tail, window, and readback plane is $A,W,K$; and the dyadic Real-seal plane is $S,R$. The structural rows $H,C,P,N$ preserve the same packet by componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\SelectedTailSeedUp}$ row.
\end{theorem}
\begin{proof}
Project the accepted carrier as $T=(Q,E,A,W,K,S,R,H,C,P,N)$. The carrier definition already displays the six dependency rows named in the chapter introduction: $\RatUp$ supplies the rational seed row $Q$, $\FiniteTailFilterUp$ supplies the selected finite-tail admission row $A$, $\StreamNameUp$ supplies the window row $W$, $\RegSeqRatUp$ supplies the readback row $K$, $\DyadicRatCoreUp$ supplies the dyadic ledger row $S$, and $\RealUp$ supplies the seal row $R$.

The row $E$ binds the rational endpoint plane by comparing the selected seed endpoint with the rational seed under the displayed rational classifier. Thus $Q,E$ form the rational endpoint plane, while $A,W,K$ form the finite-tail, window, and readback plane.

Finally use \autoref{thm:selected-tail-seed-namecert-obligations} and \autoref{thm:selected-tail-seed-real-window-handoff}. The rows $S,R$ form the dyadic Real-seal plane, and $H,C,P,N$ do not create another carrier. They transport, replay, source, and name the same finite packet, so the displayed triad is root-ready without quotient streams, host real equality, or ambient completeness.
\end{proof}

\begin{theorem}[Selected-tail seed StreamName--RegSeqRat scope]
\label{thm:selected-tail-seed-stream-regular-readback-scope}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the readback surface $W,K$ depends only on the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the packet. It does not depend on quotient-stream equality, host real equality, detached limits, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
First project the window and readback coordinates. By \autoref{def:selected-tail-seed-carrier}, $W$ is the $\StreamNameUp$ window exposing the selected stationary tail segment, and $K$ is the $\RegSeqRatUp$ readback row for the stationary regular-rational sequence at that window.

Next use \autoref{thm:selected-tail-seed-window-readback-coherence}. The readback chain consumes $W$ through $K$ inside the same finite carrier, while $H,C,P,N$ preserve, replay, source, and name that chain through the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface.

The nonescape claim follows from \autoref{thm:selected-tail-seed-real-completion-boundary}. The packet exports no quotient-stream equality, host real equality, detached limit, countable-choice selector, or ambient Real-completeness coordinate, so the $W,K$ readback scope is exactly the displayed StreamName--RegSeqRat scope.
\end{proof}

\begin{theorem}[Selected-tail seed dyadic Real-seal scope]
\label{thm:selected-tail-seed-dyadic-real-seal-scope}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the rows $S,R$ route through $\DyadicRatCoreUp$ and $\RealUp$ as a finite seal surface. This route uses the displayed dyadic tolerance ledger and Real seal only; it does not use quotient streams, host real equality, detached limits, countable choice, or ambient completeness.
\end{theorem}
\begin{proof}
Project $S$ and $R$ from the accepted carrier. The carrier definition names $S$ as the $\DyadicRatCoreUp$ tolerance and arithmetic ledger attached to the selected endpoint, and it names $R$ as the $\RealUp$ seal row obtained from the selected stationary readback.

Apply \autoref{thm:selected-tail-seed-dyadic-ledger-readback-coverage}. The passage from regular-rational readback to Real seal cannot omit $S$, so the Real-facing route passes through the displayed dyadic ledger before consuming $R$.

Finally apply \autoref{thm:selected-tail-seed-real-seal-handoff} and \autoref{thm:selected-tail-seed-real-completion-boundary}. The seal route remains a finite carrier route through $S,R$ and the structural rows that preserve the same packet. Since the carrier has no quotient stream, host real equality, detached limit, countable-choice selector, or ambient-completeness coordinate, the dyadic Real-seal scope is exactly the displayed $\DyadicRatCoreUp$--$\RealUp$ scope.
\end{proof}

\begin{theorem}[Selected-tail seed finite-tail Real-boundary scope]
\label{thm:selected-tail-seed-finite-tail-real-boundary-scope}
For every accepted $\SelectedTailSeedUp$ carrier $T=(Q,E,A,W,K,S,R,H,C,P,N)$, the tuple $A,W,K,S,R$ is the exact finite-tail-to-Real boundary consumed downstream. The finite-tail admission $A$, stream window $W$, regular-rational readback $K$, dyadic ledger $S$, and Real seal $R$ are the consumer-visible route from selected finite tail to Real-facing handoff.
\end{theorem}
\begin{proof}
Begin with the finite-tail side. By \autoref{thm:selected-tail-seed-finite-tail-admission-exactness}, every use of $W$ or $K$ first factors through the $\FiniteTailFilterUp$ admission witnessed by $A$.

Then use \autoref{thm:selected-tail-seed-window-readback-coherence}. The accepted readback chain is $W,K,S,R$: the window exposes the selected stationary segment, the regular-rational row reads it, the dyadic ledger records the finite tolerance and arithmetic, and the Real row seals the same selected endpoint.

Finally apply \autoref{thm:selected-tail-seed-real-completion-boundary}. Downstream consumers receive a finite handoff and no completion-facing principle from this chapter. Therefore $A,W,K,S,R$ is the exact finite-tail-to-Real boundary supplied by $\SelectedTailSeedUp$.
\end{proof}

This chapter is composite rather than atomic. Its independence from the sibling chapters is not expressed by row-by-row atomic separation: $\SelectedTailSeedUp$ deliberately joins $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\FiniteTailFilterUp$ into one stationary selected-tail seed packet, and each sibling omits at least one coordinate needed for the full Real-window handoff.

The Lean \texttt{TasteGate.lean} boundary for $\SelectedTailSeedUp$ must provide explicit $\mathsf{Nontrivial}\ \SelectedTailSeedUp$ and $\mathsf{FieldFaithful}\ \SelectedTailSeedUp$ instances preserving $Q,E,A,W,K,S,R,H,C,P,N$.

\falsifiablePrediction{If the finite-tail admission row $A$ or the Real seal row $R$ is absent, no accepted $\SelectedTailSeedUp$ packet can expose the stationary selected-tail endpoint as a Real-window handoff.}

\begin{theorem}[Selected-tail seed public Real-window export]
\label{thm:selected-tail-seed-public-real-window-export}
Every accepted $\SelectedTailSeedUp$ carrier exports a public Real-window handoff through the scoped rows $Q,E,A,W,K,S,R,H,C,P,N$. The export is the finite selected-tail route from rational seed and endpoint exactness through finite-tail admission, stream window, regular-rational readback, dyadic ledger, Real seal, componentwise history transport, displayed continuity replay, package provenance, and local name certificate. It excludes quotient streams, host real equality, countable choice, detached limits, and ambient Real completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier as $T=(Q,E,A,W,K,S,R,H,C,P,N)$. By \autoref{thm:selected-tail-seed-dependency-readiness-triad}, the rows split into the rational endpoint plane $Q,E$, the finite-tail readback plane $A,W,K$, the dyadic Real-seal plane $S,R$, and the structural preservation rows $H,C,P,N$.

Next apply \autoref{thm:selected-tail-seed-stream-regular-readback-scope}. The selected stationary window and regular-rational readback are already scoped by the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so the handoff has a public readback surface without quotient-stream equality or host real equality.

Apply \autoref{thm:selected-tail-seed-dyadic-real-seal-scope}. The same route then passes through the displayed $\DyadicRatCoreUp$ ledger and $\RealUp$ seal, so the L10 source chain remains finite and carrier-internal.

Finally use \autoref{thm:selected-tail-seed-finite-tail-real-boundary-scope}. Downstream consumers receive exactly the boundary $A,W,K,S,R$, while $Q,E,H,C,P,N$ give the seed, comparison, transport, replay, provenance, and naming context for that boundary. Since the cited scope theorems rule out quotient streams, host real equality, countable choice, detached limits, and ambient Real completeness, this is the public Real-window export promised by the accepted $\SelectedTailSeedUp$ carrier.
\end{proof}

\begin{theorem}[Selected-tail seed Real-completion bridge]
\label{thm:selected-tail-seed-real-completion-bridge}
The public Real-window export of \autoref{thm:selected-tail-seed-public-real-window-export} is exactly the finite bridge route consumed by the stationary rational selected-tail seed exactness surface of \autoref{thm:real-completeness-stationary-rational-selected-tail-seed-exactness}. The route passes through
$$
Q,E,A,W,K,S,R,H,C,P,N
$$
and its sibling dependencies are precisely $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, and $\FiniteTailFilterUp$. It excludes quotient streams, host real equality, countable choice, detached limits, and ambient Real completeness.
\end{theorem}
\begin{proof}
Start with the public export. By \autoref{thm:selected-tail-seed-public-real-window-export}, every accepted carrier already presents the route $Q,E,A,W,K,S,R,H,C,P,N$ as a public Real-window handoff, with the rational seed and endpoint comparison in $Q,E$, the selected finite-tail readback in $A,W,K$, the dyadic Real-seal surface in $S,R$, and the structural rows in $H,C,P,N$.

The admission side is fixed by \autoref{thm:selected-tail-seed-finite-tail-admission-exactness}. No consumer can reach the selected stationary stream window or regular-rational readback before passing through the displayed $\FiniteTailFilterUp$ row $A$, so the bridge cannot insert an alternate raw-tail or detached-limit path.

Next use \autoref{thm:selected-tail-seed-stream-regseq-dyadic-compatibility}. The rows $W,K,S$ form the required $\StreamNameUp$--$\RegSeqRatUp$--$\DyadicRatCoreUp$ chain before the Real seal is read, while \autoref{thm:selected-tail-seed-dyadic-real-seal-scope} keeps the seal route inside the displayed $\DyadicRatCoreUp$ and $\RealUp$ rows.

Finally apply \autoref{thm:selected-tail-seed-real-seal-handoff} and \autoref{thm:selected-tail-seed-real-completion-boundary}. These results hand the selected endpoint to $R$ without adding quotient streams, host real equality, countable choice, detached limits, or ambient Real completeness. Thus the exactness surface of \autoref{thm:real-completeness-stationary-rational-selected-tail-seed-exactness} consumes precisely the same finite route exported by \autoref{thm:selected-tail-seed-public-real-window-export}.
\end{proof}

\begin{theorem}[Selected-tail seed mature Real-completion package]
\label{thm:selected-tail-seed-mature-real-completion-package}
The public export, finite-tail admission exactness, $\StreamNameUp$--$\RegSeqRatUp$--$\DyadicRatCoreUp$ compatibility, dyadic Real-seal scope, and Real-completion bridge together form the mature finite selected-tail package over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\FiniteTailFilterUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The package excludes quotient streams, host real equality, countable choice, detached limit selection, and ambient Real completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:selected-tail-seed-public-real-window-export}. It provides the public route through $Q,E,A,W,K,S,R,H,C,P,N$ and already records the exclusion of quotient streams, host real equality, countable choice, detached limits, and ambient Real completeness.

The finite-tail and sibling compatibility rows are fixed by \autoref{thm:selected-tail-seed-finite-tail-admission-exactness} and \autoref{thm:selected-tail-seed-stream-regseq-dyadic-compatibility}. These results bind the $\FiniteTailFilterUp$ admission and the $\StreamNameUp$--$\RegSeqRatUp$--$\DyadicRatCoreUp$ readback chain inside the accepted carrier.

Finally use \autoref{thm:selected-tail-seed-dyadic-real-seal-scope} and \autoref{thm:selected-tail-seed-real-completion-bridge}. The Real-facing seal remains the displayed $\DyadicRatCoreUp$--$\RealUp$ finite route, and the bridge consumed by the stationary rational selected-tail exactness surface is precisely the same route. Thus the cited rows constitute the mature finite selected-tail Real-completion package, with no additional quotient, host-equality, choice, detached-limit, or ambient-completeness principle.
\end{proof}

\closureat{SelectedTailSeedUp}{seedStr}
\closureat{SelectedTailSeedUp}{obligationStr}
\closureat{SelectedTailSeedUp}{scopedStr}
\closureat{SelectedTailSeedUp}{publicStr}
\closureat{SelectedTailSeedUp}{bridgedStr}
\closureat{SelectedTailSeedUp}{matureStr}

\begin{closurestatus}{\SelectedTailSeedUp}
  \constructivestory{A $\SelectedTailSeedUp$ packet is generated from a rational seed row, selected endpoint exactness, finite-tail admission, stream window, regular-rational readback, dyadic tolerance ledger, Real seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:selected-tail-seed-dependency-readiness-triad}, \autoref{thm:selected-tail-seed-stream-regular-readback-scope}, \autoref{thm:selected-tail-seed-dyadic-real-seal-scope}, \autoref{thm:selected-tail-seed-finite-tail-real-boundary-scope}, \autoref{thm:selected-tail-seed-public-real-window-export}, \autoref{thm:selected-tail-seed-real-completion-bridge}, and \autoref{thm:selected-tail-seed-mature-real-completion-package} bind the mature finite selected-tail Real-completion package over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\FiniteTailFilterUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.SelectedTailSeedUp.SelectedTailSeedTasteGate\_single\_carrier\_alignment}
  \bridgestatus{none}
  \origin{ai}
  \leanchecked{BEDC.Derived.SelectedTailSeedUp.taste\_gate}
  \notclaimed{This chapter does not close bridge checking, quotient streams, host real equality, countable choice, detached limit selection, or ambient Real completeness.}
  \upgradepath{Further verification requires bridge checking for the selected-tail Real-completion route without quotient streams, host real equality, countable choice, detached limits, or ambient Real completeness.}
\end{closurestatus}
