\chapter{A Concrete Naming Certificate for $\DyadicToleranceTriangleLedgerUp$}
\label{ch:concrete-instances-dyadic-tolerance-triangle-ledger-namecert}
\origin{ai}

The $\DyadicToleranceTriangleLedgerUp$ packet realizes the three-leg diagonal-regularity estimate of \autoref{thm:real-completeness-diagonal-regular} inside the Real-completeness route of \autoref{ch:visions-real-completeness}. It is a dyadic ledger layer over the existing $\RegularCauchyTriangleBoundUp$ estimate of \autoref{ch:concrete-instances-regular-cauchy-triangle-bound-namecert}: $\DyadicRatCoreUp$ supplies tolerance arithmetic through \autoref{ch:concrete-instances-dyadicratcore-namecert}, $\StreamNameUp$ supplies the finite diagonal and intermediate windows through \autoref{ch:concrete-instances-streamname-namecert}, $\RegSeqRatUp$ supplies endpoint regularity reads through \autoref{ch:concrete-instances-regseqrat-namecert}, and $\RealUp$ is the downstream seal surface of \autoref{ch:concrete-instances-real-namecert}. The packet does not select a limit, quotient a stream, or appeal to ambient completeness; it records the finite tolerance rows that the diagonal proof must read before the Real-facing handoff.

\begin{definition}[Dyadic tolerance triangle ledger carrier]
\label{def:dyadic-tolerance-triangle-ledger-carrier}
A $\DyadicToleranceTriangleLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D_m$ and $D_n$ are the two $\StreamNameUp$ diagonal observation rows for the requested indices $m$ and $n$.
\item $I_m$ and $I_n$ are the two intermediate $\StreamNameUp$ rows used by the diagonal-regularity triangle.
\item $E_m$ and $E_n$ are the endpoint $\RegSeqRatUp$ regularity reads for the legs $D_m \longrightarrow I_m$ and $I_n \longrightarrow D_n$.
\item $M$ is the middle Cauchy-modulus read for the leg $I_m \longrightarrow I_n$.
\item $Q$ is the $\DyadicRatCoreUp$ ledger carrying the two endpoint tolerances, the middle tolerance, and the displayed dyadic output bound.
\item $T$ is the consumed $\RegularCauchyTriangleBoundUp$ row that assembles the same three legs as one diagonal estimate.
\item $H$ records componentwise $\hsame$ transport for the four window rows, the three leg rows, the dyadic ledger, the consumed triangle-bound row, provenance, and the local name.
\item $C$ records displayed $\Cont$ routes for reading endpoint legs, reading the middle leg, summing dyadic tolerances, checking the consumed triangle-bound row, and handing the packet to the Real-facing diagonal consumer.
\item $P$ is the $\Pkg$ provenance over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularCauchyTriangleBoundUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\DyadicToleranceTriangleLedgerUp}$ row.
\end{enumerate}
The carrier has no coordinate for a missing endpoint leg, a missing middle modulus leg, quotient stream equality, host real equality, selected limits, or ambient completeness.
\end{definition}

\begin{definition}[Dyadic tolerance triangle ledger classifier]
\label{def:dyadic-tolerance-triangle-ledger-classifier}
Two accepted $\DyadicToleranceTriangleLedgerUp$ carriers classify as the same ledger only when their four $\StreamNameUp$ windows, two $\RegSeqRatUp$ endpoint reads, middle modulus read, $\DyadicRatCoreUp$ tolerance row, consumed $\RegularCauchyTriangleBoundUp$ row, and $\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows are componentwise transported by the displayed $\hsame$ data. The classifier does not identify packets by host equality of real numbers, by quotienting streams, or by forgetting one of the three triangle legs.
\end{definition}

\begin{theorem}[Dyadic tolerance triangle ledger obligations]
\label{thm:dyadic-tolerance-triangle-ledger-obligations}
For every accepted $\DyadicToleranceTriangleLedgerUp$ carrier $L=(D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N)$, the local $\NameCert_{\DyadicToleranceTriangleLedgerUp}$ surface consists exactly of carrier exposure, classifier transport, endpoint-leg coverage for $E_m,E_n$, middle-leg coverage for $M$, dyadic tolerance addition through $Q$, consumed $\RegularCauchyTriangleBoundUp$ compatibility through $T$, Real-facing continuation through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicToleranceTriangleLedgerUp.DyadicToleranceTriangleLedger\_window\_endpoint\_separation}
\begin{proof}
Carrier exposure is projection from \autoref{def:dyadic-tolerance-triangle-ledger-carrier}. The displayed rows name the two diagonal windows, the two intermediate windows, the two endpoint legs, the middle leg, the dyadic ledger, the consumed triangle-bound packet, and the support rows.

Classifier transport is exactly the relation of \autoref{def:dyadic-tolerance-triangle-ledger-classifier}. It keeps the four windows, three leg rows, dyadic ledger, consumed triangle-bound row, and support rows on one componentwise transported surface.

The endpoint and middle obligations are then read from the sibling surfaces. The endpoint reads use $\RegSeqRatUp$ through \autoref{ch:concrete-instances-regseqrat-namecert}; the middle read is the Cauchy-modulus leg already assembled by \autoref{ch:concrete-instances-regular-cauchy-triangle-bound-namecert}; and the tolerance addition is the $\DyadicRatCoreUp$ row of \autoref{ch:concrete-instances-dyadicratcore-namecert}.

Finally $C,P,N$ hand this finite ledger to the $\RealUp$ diagonal consumer. Since the carrier omits quotient streams, selected limits, host real equality, missing-leg shortcuts, and ambient completeness, the listed rows exhaust the local certificate surface.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger nonescape]
\label{thm:dyadic-tolerance-triangle-ledger-nonescape}
Every diagonal-regularity consumer of an accepted $\DyadicToleranceTriangleLedgerUp$ packet reads the two endpoint legs $E_m,E_n$, the middle Cauchy-modulus leg $M$, the dyadic tolerance ledger $Q$, the consumed triangle-bound row $T$, and the displayed $\BHist/\hsame/\Cont/\Pkg/\NameCert$ support rows. It cannot replace any leg by a host real equality, quotient-stream comparison, selected limit, detached completion witness, or ambient completeness row.
\end{theorem}
\begin{proof}
Begin with the obligation surface of \autoref{thm:dyadic-tolerance-triangle-ledger-obligations}. It exposes the two endpoint legs, the middle leg, the tolerance ledger, and the consumed triangle-bound row as required rows of the local certificate.

Use the classifier of \autoref{def:dyadic-tolerance-triangle-ledger-classifier}. A consumer that transports the ledger must transport all three leg rows and the dyadic output row together; forgetting one leg changes the accepted packet.

The excluded objects have no coordinate in \autoref{def:dyadic-tolerance-triangle-ledger-carrier}. Therefore no continuation route can export host equality, quotient-stream comparison, selected limits, detached completion witnesses, or ambient completeness in place of the displayed three-leg ledger.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger window handoff]
\label{thm:dyadic-tolerance-triangle-ledger-window-handoff}
Every $\RealUp$ or diagonal-limit consumer that uses a $\DyadicToleranceTriangleLedgerUp$ packet receives the finite handoff
$$
D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N
$$
after the four $\StreamNameUp$ windows have been read and before any Real seal is consumed. The handoff realizes the three-leg estimate of \autoref{thm:real-completeness-diagonal-regular} as finite $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
First read the carrier. The four window rows $D_m,D_n,I_m,I_n$ are the only stream observations available to the packet, and the leg rows $E_m,E_n,M$ are attached to those windows.

Next apply the obligation theorem. It requires the dyadic output bound to be read through $Q$ and the compatibility with the existing three-leg estimate to be read through $T$.

Finally use non-escape. Since no selected limit, quotient stream, host real equality, detached completion witness, or ambient completeness row can be exported, the Real-facing consumer receives exactly the displayed finite handoff.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger middle-leg coverage]
\label{thm:dyadic-tolerance-triangle-ledger-middle-leg-coverage}
For every accepted $\DyadicToleranceTriangleLedgerUp$ carrier $L=(D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N)$, the row $M$ is the only admissible middle Cauchy-modulus leg. Any accepted consumer of $L$ that reaches from $I_m$ to $I_n$ must read $M$ through the displayed $\Cont$ route and cannot replace it by an endpoint regularity row, a quotient stream equality, a selected limit, a detached completion witness, or ambient completeness.
\end{theorem}
\begin{proof}
Read the carrier of \autoref{def:dyadic-tolerance-triangle-ledger-carrier}. Among the displayed rows, only $M$ is assigned to the leg $I_m \longrightarrow I_n$; the rows $E_m$ and $E_n$ are bound to the two endpoint legs, and no extra coordinate records a second middle modulus.

Use the classifier of \autoref{def:dyadic-tolerance-triangle-ledger-classifier}. Componentwise $\hsame$ transport keeps the middle leg as the $M$ coordinate, so a transported packet cannot silently exchange $M$ for an endpoint row or for an external real-completion witness.

Finally apply non-escape from \autoref{thm:dyadic-tolerance-triangle-ledger-nonescape}. The excluded host, quotient, limit-selection, detached-completion, and ambient-completeness objects have no coordinate in the packet, hence no accepted middle-leg consumer can read them in place of $M$.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger tolerance addition]
\label{thm:dyadic-tolerance-triangle-ledger-tolerance-addition}
For every accepted $\DyadicToleranceTriangleLedgerUp$ carrier $L=(D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N)$, the row $Q$ is the only dyadic tolerance-addition ledger combining the two endpoint tolerances and the middle tolerance. The packet exposes no second dyadic output row and no route that can compute the displayed output bound outside $\DyadicRatCoreUp$.
\end{theorem}
\begin{proof}
The carrier assigns exactly one row to dyadic tolerance addition, namely $Q$. The endpoint tolerances are supplied by $E_m$ and $E_n$, the middle tolerance is supplied by $M$, and the displayed output bound is part of the same $\DyadicRatCoreUp$ ledger row.

Classifier transport preserves $Q$ as the dyadic ledger coordinate. Thus a consumer that transports the accepted packet must transport the endpoint tolerances, the middle tolerance, and the output bound together rather than recomputing one of them through a detached route.

The non-escape theorem blocks the remaining shortcuts. Since the packet has no coordinate for host real equality, quotient streams, selected limits, detached completion witnesses, or ambient completeness, the only accepted tolerance-addition read is the $Q$ row.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger triangle-bound compatibility]
\label{thm:dyadic-tolerance-triangle-ledger-triangle-bound-compatibility}
For every accepted $\DyadicToleranceTriangleLedgerUp$ carrier $L=(D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N)$, the consumed row $T$ uses the same three legs $E_m,E_n,M$ as the $\RegularCauchyTriangleBoundUp$ packet. It may package the three-leg estimate for the Real-facing handoff, but it cannot introduce a fourth leg, omit the middle leg, or identify endpoint and middle evidence by host equality.
\end{theorem}
\begin{proof}
The carrier binds $T$ as the consumed $\RegularCauchyTriangleBoundUp$ row and lists exactly three leg rows beside it: $E_m$, $E_n$, and $M$. These are the two endpoint regularity reads and the middle Cauchy-modulus read used by the diagonal-regularity triangle.

The obligation theorem forces compatibility through the same displayed rows. It does not expose an independent triangle-bound coordinate that could ignore $M$ or introduce a fourth leg.

The window handoff theorem then sends $D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N$ to the Real-facing consumer as one finite packet. Because non-escape forbids host equality and quotient-stream replacement, $T$ remains compatible with the same three concrete legs.
\end{proof}

\begin{theorem}[Dyadic tolerance triangle ledger tastegate obligation closure]
\label{thm:dyadic-tolerance-triangle-ledger-tastegate-obligation-closure}
The $\DyadicToleranceTriangleLedgerUp$ packet is obligation-closed for its displayed L10 ledger surface. The carrier, classifier, nonescape theorem, window handoff, falsifiable prediction, independence witness, Lean \texttt{ChapterTasteGate}, $\mathsf{Nontrivial}\ \DyadicToleranceTriangleLedgerUp$, and $\mathsf{FieldFaithful}\ \DyadicToleranceTriangleLedgerUp$ evidence jointly bind the rows $D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N$ as the local $\NameCert_{\DyadicToleranceTriangleLedgerUp}$ obligation surface.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicToleranceTriangleLedgerUp.taste\_gate}
\begin{proof}
Carrier and classifier exposure are supplied by \autoref{def:dyadic-tolerance-triangle-ledger-carrier} and \autoref{def:dyadic-tolerance-triangle-ledger-classifier}. The aggregate obligation theorem names the endpoint, middle, dyadic-addition, triangle-bound, Real-continuation, package, and local-name clauses.

The three separated compatibility theorems above isolate the middle leg $M$, the dyadic addition row $Q$, and the consumed triangle-bound row $T$. Together with endpoint separation, they make the finite ledger surface checkable row by row.

Nonescape and window handoff then bind the consumer behavior: no quotient stream, selected limit, host equality, detached completion witness, or ambient-completeness row can replace the displayed finite packet.

Finally the falsifiable prediction and independence witness record the negative tests, while the checked Lean \texttt{ChapterTasteGate} supplies the formal gate together with its $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ evidence. These ingredients exhaust the stated obligation surface without claiming a public Real-completion seal.
\end{proof}

\falsifiablePrediction{A diagonal-regularity consumer that omits one of the two endpoint legs or the middle Cauchy-modulus leg refutes the packet.}

\independenceWitness{dyadicratcore, streamname, regseqrat, real, regular-cauchy-triangle-bound: none is bijective to $\DyadicToleranceTriangleLedgerUp$, because the dyadic core lacks stream windows, the stream-name surface lacks rational tolerance addition, the regular-rational surface lacks the middle Cauchy-modulus leg, the Real surface is downstream of the seal, and the regular-cauchy triangle-bound packet does not isolate the dyadic tolerance ledger as its own classifier and Real-window handoff.}

Lean \texttt{TasteGate.lean} for $\DyadicToleranceTriangleLedgerUp$ must provide explicit $\mathsf{Nontrivial}\ \DyadicToleranceTriangleLedgerUp$ and $\mathsf{FieldFaithful}\ \DyadicToleranceTriangleLedgerUp$ instances for $D_m,D_n,I_m,I_n,E_m,E_n,M,Q,T,H,C,P,N$.

\closureat{DyadicToleranceTriangleLedgerUp}{obligationStr}

\begin{closurestatus}{\DyadicToleranceTriangleLedgerUp}
  \constructivestory{A $\DyadicToleranceTriangleLedgerUp$ packet is generated from four stream windows, two endpoint regularity reads, one middle Cauchy-modulus read, a dyadic tolerance-addition ledger, a consumed RegularCauchyTriangleBound row, componentwise hsame transport, displayed Cont routes, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:dyadic-tolerance-triangle-ledger-carrier}, \autoref{def:dyadic-tolerance-triangle-ledger-classifier}, \autoref{thm:dyadic-tolerance-triangle-ledger-obligations}, \autoref{thm:dyadic-tolerance-triangle-ledger-nonescape}, \autoref{thm:dyadic-tolerance-triangle-ledger-window-handoff}, \autoref{thm:dyadic-tolerance-triangle-ledger-middle-leg-coverage}, \autoref{thm:dyadic-tolerance-triangle-ledger-tolerance-addition}, \autoref{thm:dyadic-tolerance-triangle-ledger-triangle-bound-compatibility}, and \autoref{thm:dyadic-tolerance-triangle-ledger-tastegate-obligation-closure} bind the finite dyadic ledger surface for the diagonal-regularity triangle.}
  \formalstatus{\theoremCheckedV}
  \leantarget{BEDC.Derived.DyadicToleranceTriangleLedgerUp.taste\_gate}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close bridge checking, scoped downstream Real-completion closure, the full Real-completeness theorem, quotient stream equality, selected limits, host real equality, detached completion witnesses, or ambient completeness.}
  \upgradepath{Scoped closure requires downstream diagonal-regularity consumers to reuse the same endpoint rows, middle row, dyadic tolerance row, triangle-bound row, and Real-window handoff without adding nonlocal witnesses.}
\end{closurestatus}
