\chapter{A Concrete Naming Certificate for $\ScientificObjectUp$}
\label{ch:concrete-instances-scientificobject-namecert}
\origin{ai}

The $\ScientificObjectUp$ packet realizes the scientific-object surface of \autoref{def:philosophy-scientific-object} and \autoref{def:philosophy-scientific-object-five-sources} as finite BEDC NameCert data. It sits after the physical-model audit of \autoref{ch:concrete-instances-physical-model-audit-namecert}, the truth-certificate route of \autoref{ch:concrete-instances-reality-constrained-truth-cert-namecert}, the open-fit packet of \autoref{ch:concrete-instances-open-fit-packet-namecert}, the domain truth certificate of \autoref{ch:concrete-instances-domain-truth-certificate-namecert}, and the inter-history transport seal of \autoref{ch:concrete-instances-inter-hist-transport-seal-namecert}. These siblings provide audit, truth, finite-fit, domain, and invariant rows; this packet binds them into one object-facing carrier before any consumer reads a scientific object as mature.

\begin{definition}[Scientific object carrier]
\label{def:scientific-object-carrier}
A $\ScientificObjectUp$ carrier is a finite $\BHist$ packet
$$
S=(R,K,I,L,B,G,A,T,O,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $R$ records the source histories, measurement rows, continuations, or instrument traces that generate the object.
\item $K$ is the classifier row specifying which records count as the same object-state presentation.
\item $I$ is the inter-history invariant row, read through the transport and invariant discipline of $\InterHistInvariantUp$.
\item $L$ is the empirical ledger row recording compression, averaging, calibration, fitting, projection, residue, and observed failure data.
\item $B$ is the bridge row to a mathematical or scientific model, including the optional model-facing route through $\OpenFitPacketUp$ and $\RealityConstrainedTruthCertUp$.
\item $G$ is the gap-report row listing unclosed prediction, domain, bridge, and falsification commitments.
\item $A$ is the $\PhysicalModelAuditUp$ row exposing source traces, observed signatures, model signatures, classifier comparison, tower data, failure surface, and audit strength.
\item $T$ is the $\RealityConstrainedTruthCertUp$ row exposing the truth-certificate source, signature, classifier, tower, stability, descent, invariant, ledger, and failure fields.
\item $O$ is the $\OpenFitPacketUp$ row exposing finite fit, finite defeat, continuation scope, and open residue.
\item $D$ is the $\DomainTruthCertificateUp$ row exposing the domain in which the object-facing truth claim may be read.
\item $H$ records componentwise $\hsame$ transport for $R,K,I,L,B,G,A,T,O,D$ and the local certificate row.
\item $C$ records displayed $\Cont$ replay from record admission through classifier, invariant, ledger, bridge, gap report, audit, truth, open fit, domain, transport, provenance, and local name.
\item $P$ is the $\Pkg$ provenance over $\ScientificObjectUp$, $\PhysicalModelAuditUp$, $\RealityConstrainedTruthCertUp$, $\OpenFitPacketUp$, $\DomainTruthCertificateUp$, $\InterHistInvariantUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\ScientificObjectUp}$ row.
\end{enumerate}
The carrier has no coordinate for bare object existence, unledgered empirical fit, hidden model identity, global synchronization, or final physical truth outside the displayed rows.
\end{definition}
\leanchecked{BEDC.Derived.ScientificObjectUp.ScientificObjectUp\_single\_carrier\_alignment}

\begin{definition}[Scientific object NameCert obligations]
\label{def:scientific-object-namecert-obligations}
For the carrier of \autoref{def:scientific-object-carrier}, the local $\NameCert_{\ScientificObjectUp}$ surface consists exactly of carrier admission for $S$, record exposure through $R$, classifier exposure through $K$, inter-history invariant exposure through $I$, empirical-ledger exposure through $L$, bridge exposure through $B$, gap-report exposure through $G$, audit exposure through $A$, reality-constrained truth exposure through $T$, open-fit exposure through $O$, domain exposure through $D$, componentwise transport through $H$, displayed replay through $C$, provenance through $P$, and local naming through $N$.
\end{definition}

\begin{theorem}[Scientific object gap-report ledger]
\label{thm:scientific-object-gap-report-ledger}
Every accepted $\ScientificObjectUp$ packet exposes its gap report $G$ before the local name $N$ is readable. A consumer may not replace $G$ by the empirical ledger $L$, the model bridge $B$, the physical-model audit $A$, the truth-certificate row $T$, or the domain certificate $D$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:scientific-object-carrier}. The gap report is a named coordinate of the accepted packet, separate from the record, classifier, invariant, ledger, bridge, audit, truth, open-fit, and domain rows.

Apply \autoref{def:scientific-object-namecert-obligations}. The local NameCert surface lists $G$ as an obligation before provenance and local naming are available. The empirical ledger records what has been fitted or compressed, the bridge records model correspondence, the audit records signature comparison, the truth certificate records a reality-constrained claim, and the domain certificate records where that claim may be read.

None of those rows lists the unclosed prediction, domain, bridge, and falsification commitments as the gap-report coordinate. Therefore a consumer that omits $G$ reads only a projection of the scientific-object packet, not an accepted $\ScientificObjectUp$ object name.
\end{proof}

\begin{theorem}[Scientific object empirical-bridge separation]
\label{thm:scientific-object-empirical-bridge-separation}
In every accepted $\ScientificObjectUp$ packet, the empirical ledger $L$ and bridge row $B$ are distinct obligation surfaces. The bridge may use $\OpenFitPacketUp$, $\RealityConstrainedTruthCertUp$, and $\DomainTruthCertificateUp$ routes, but it does not discharge record exposure, invariant exposure, ledger residue, audit strength, or the gap report by itself.
\end{theorem}
\begin{proof}
Read the carrier coordinates. The empirical ledger $L$ records compression, averaging, calibration, fitting, projection, residue, and observed failure data, while $B$ records the model-facing bridge.

The sibling rows are downstream supports for bridge discipline. $\OpenFitPacketUp$ supplies finite-fit and finite-defeat visibility, $\RealityConstrainedTruthCertUp$ supplies the truth-certificate route, and $\DomainTruthCertificateUp$ supplies the allowed domain of the truth read. These rows do not identify the bridge with the empirical ledger or with the inter-history invariant.

The NameCert obligations keep $R,K,I,L,B,G,A,T,O,D$ as separate rows. Thus an accepted object may have a bridge only together with the ledger, audit, invariant, and gap-report surfaces that make the scientific-object name non-vacuous.
\end{proof}

\begin{theorem}[Scientific object NameCert surface]
\label{thm:scientific-object-namecert-surface}
Every accepted $\ScientificObjectUp$ object read factors through
$$
R,K,I,L,B,G,A,T,O,D,H,C,P,N.
$$
The consumer receives a finite record, classifier, invariant, empirical ledger, bridge, gap report, audit, truth-certificate, open-fit, domain, transport, replay, provenance, and local NameCert packet. It receives no bare scientific object, unrecorded empirical adequacy, host-model identity, final truth oracle, or hidden bridge completion.
\end{theorem}
\begin{proof}
Start from the obligation surface of \autoref{def:scientific-object-namecert-obligations}. It exhausts the local certificate by the displayed record, classifier, invariant, ledger, bridge, gap-report, audit, truth, open-fit, domain, transport, replay, provenance, and local-name rows.

Use \autoref{thm:scientific-object-gap-report-ledger} to keep unclosed commitments visible, and use \autoref{thm:scientific-object-empirical-bridge-separation} to keep empirical fit and bridge status distinct.

The structural rows $H,C,P,N$ transport, replay, source, and name the same displayed packet. They do not create a hidden object coordinate or an unrecorded truth route. Hence every accepted object read factors through the stated finite route.
\end{proof}
\leanchecked{BEDC.Derived.ScientificObjectUp.ScientificObjectTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Scientific object record-classifier admission]
\label{thm:scientific-object-record-classifier-admission}
Every accepted $\ScientificObjectUp$ packet first exposes its record row $R$ and classifier row $K$. The carrier transport through $H$ and the displayed replay through $C$ are available before any consumer reads the empirical ledger $L$, bridge row $B$, truth row $T$, domain row $D$, gap report $G$, provenance row $P$, or local name row $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:scientific-object-carrier}. The displayed packet starts with $R$ and $K$, and its structural rows $H$ and $C$ record componentwise $\hsame$ transport and $\Cont$ replay for the same finite data.

Apply \autoref{def:scientific-object-namecert-obligations}. Carrier admission, record exposure, and classifier exposure are listed before the later ledger, bridge, gap-report, audit, truth, open-fit, domain, provenance, and local-name reads. Thus a consumer cannot reach the object-facing rows while bypassing the record and classifier admission surface.
\end{proof}

\begin{theorem}[Scientific object truth-domain gap scope]
\label{thm:scientific-object-truth-domain-gap-scope}
In every accepted $\ScientificObjectUp$ packet, the truth row $T$, domain row $D$, and gap-report row $G$ remain separate scoped obligations. The reality-constrained truth route is readable only through the domain row, and neither row discharges the gap report.
\end{theorem}
\begin{proof}
Use \autoref{thm:scientific-object-gap-report-ledger}. The gap report $G$ is a named coordinate before the local name and cannot be replaced by the empirical ledger, bridge, audit, truth, or domain rows.

Use \autoref{thm:scientific-object-empirical-bridge-separation}. The reality-constrained truth row and the domain certificate row support the model-facing route, but the bridge does not discharge record exposure, invariant exposure, ledger residue, audit strength, or the gap report.

Therefore $T$ supplies only the reality-constrained truth surface, $D$ supplies the domain in which that surface may be read, and $G$ remains the separate report of unclosed prediction, domain, bridge, and falsification commitments.
\end{proof}

\begin{theorem}[Scientific object obligation-closure package]
\label{thm:scientific-object-obligation-closure-package}
The carrier, record-classifier admission, gap-report ledger, empirical-bridge separation, truth-domain scope, NameCert surface, falsifiability row, and independence row together provide the paper-side obligation package for $\ScientificObjectUp$. Every accepted object read is constrained by
$$
R,K,I,L,B,G,A,T,O,D,H,C,P,N
$$
and by the displayed refusal of bare object existence, unledgered empirical fit, hidden model identity, global synchronization, and final physical truth outside those rows.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:scientific-object-carrier} displays all finite rows in the package and states the absent coordinates. Apply \autoref{thm:scientific-object-record-classifier-admission} to force record and classifier admission before downstream object reads.

Apply \autoref{thm:scientific-object-gap-report-ledger}, \autoref{thm:scientific-object-empirical-bridge-separation}, and \autoref{thm:scientific-object-truth-domain-gap-scope}. These results keep the gap ledger, empirical bridge, truth route, and domain scope as separate obligations.

Finally apply \autoref{thm:scientific-object-namecert-surface}. The falsifiability row rejects consumers that omit the gap report, empirical ledger, inter-history invariant, or reality-constrained truth rows, and the independence row records that the named siblings supply constituent surfaces rather than the full carrier. The listed rows therefore form the paper-side obligation package for $\ScientificObjectUp$.
\end{proof}

\falsifiablePrediction{Any accepted ScientificObjectUp consumer that exports a mature scientific object while omitting the gap report, empirical ledger, inter-history invariant, or reality-constrained truth rows refutes the packet.}

\independenceWitness{physicalmodelaudit, realityconstrainedtruthcert, openfitpacket, domaintruthcertificate, interhistinvariant: none is bijective because $\ScientificObjectUp$ binds records, classifier, invariant, ledger, bridge, gap report, audit, truth, open-fit, domain, transport, provenance, and local NameCert rows in one carrier, while each sibling supplies only one constituent surface.}

The Lean TasteGate path \texttt{lean4/BEDC/Derived/ScientificObjectUp/TasteGate.lean} provides explicit $\Nontrivial\ \ScientificObjectUp$ and $\FieldFaithful\ \ScientificObjectUp$ instances. These instances distinguish record, classifier, invariant, empirical-ledger, bridge, gap-report, audit, truth-certificate, open-fit, domain, transport, replay, provenance, and local NameCert rows.

\closureat{ScientificObjectUp}{seedStr}
\closureat{ScientificObjectUp}{obligationStr}
\closureat{ScientificObjectUp}{scopedStr}[BEDC.Derived.ScientificObjectUp.taste\_gate]

\begin{closurestatus}{\ScientificObjectUp}
  \constructivestory{A $\ScientificObjectUp$ packet is generated from finite record, classifier, invariant, empirical ledger, bridge, gap report, audit, truth, open-fit, domain, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and local $\NameCert$ rows.}
  \leanchecked{BEDC.Derived.ScientificObjectUp.taste\_gate}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:scientific-object-carrier}, \autoref{thm:scientific-object-record-classifier-admission}, \autoref{thm:scientific-object-truth-domain-gap-scope}, \autoref{thm:scientific-object-namecert-surface}, and \autoref{thm:scientific-object-obligation-closure-package} bind the carrier, record-classifier admission, truth-domain gap scope, NameCert surface, and obligation package as the finite scoped surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, final physical truth, unledgered empirical adequacy, or hidden bridge completion.}
  \upgradepath{Obligation closure requires checked carrier admission, gap-report ledger, empirical-bridge separation, NameCert surface, TasteGate nontriviality, and field faithfulness for $R,K,I,L,B,G,A,T,O,D,H,C,P,N$.}
\end{closurestatus}
