\chapter{A Concrete Naming Certificate for $\FiniteRealSectionUp$}
\label{ch:concrete-instances-finite-real-section-namecert}
\origin{ai}

The $\FiniteRealSectionUp$ packet realizes one finite section of the diagonal-limit representative of \autoref{def:real-completeness-diagonal-limit}. It sits between the representative packet of \autoref{ch:concrete-instances-diagonallimitrepresentative-namecert} and the tail-alignment packet of \autoref{ch:concrete-instances-tail-modulus-alignment-namecert}, and it consumes the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the seal rows of \autoref{ch:concrete-instances-real-namecert}. The packet names a single displayed precision request and its section route; it is not a quotient stream, selected host limit, countable-choice selector, ambient Real-completeness principle, or standard bridge.

\begin{definition}[Finite real section carrier]
\label{def:finite-real-section-carrier}
A $\FiniteRealSectionUp$ carrier is a finite $\BHist$ packet
$$
S=(q,W,R,D,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $q$ is the finite precision request for the diagonal-limit section;
\item $W$ is the $\StreamNameUp$ window exposing the selected stream read for that request;
\item $R$ is the $\RegSeqRatUp$ readback row read through $W$;
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger recording the rational arithmetic and error budget attached to $R$;
\item $E$ is the $\RealUp$ seal row reached after the selected regular-rational readback has been repacked through $D$;
\item $H$ records componentwise $\hsame$ transport for $q,W,R,D,E$ and the local certificate row;
\item $C$ records displayed $\Cont$ replay from the request through the window, readback, dyadic ledger, and Real seal;
\item $P$ is the $\Pkg$ provenance over $\FiniteRealSectionUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\FiniteRealSectionUp}$ row.
\end{enumerate}
The carrier exports only the displayed finite-section route and its transport, replay, provenance, and naming support.
\end{definition}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSectionTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite real section obligation surface]
\label{thm:finite-real-section-obligation-surface}
For the carrier of \autoref{def:finite-real-section-carrier}, the local $\NameCert_{\FiniteRealSectionUp}$ surface consists exactly of carrier admission, classifier stability for the displayed tuple $(q,W,R,D,E)$, window-readback compatibility between $W$ and $R$, dyadic-tolerance exposure through $D$, $\RealUp$ seal exposure through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_transport\_stability}
\begin{proof}
Project the carrier $S$. Its coordinates list one precision request, one stream window, one regular-rational readback, one dyadic ledger, one Real seal, transport, replay, provenance, and local naming rows.

The data-bearing obligations are inherited in order. Carrier admission exposes $q$; the classifier is stable precisely because accepted packets compare the displayed tuple $(q,W,R,D,E)$ componentwise before any support row is read; the window-readback obligation then forces $R$ to be the readback attached to $W$.

The remaining rows are downstream support. The dyadic ledger $D$ records the tolerance row for the readback, the seal row $E$ is reachable only after that ledger is displayed, and $H,C,P,N$ only transport, replay, source, and name the same finite route. Thus the listed obligations exhaust the local naming surface.
\end{proof}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_obligation\_surface}

\begin{theorem}[Finite real section window-readback determinacy]
\label{thm:finite-real-section-window-readback-determinacy}
For an accepted $\FiniteRealSectionUp$ carrier $S=(q,W,R,D,E,H,C,P,N)$ of \autoref{def:finite-real-section-carrier}, the precision request $q$ determines the displayed $\StreamNameUp$ window $W$, and the $\RegSeqRatUp$ row $R$ is read only through that same window. No second stream window, quotient stream, or host sequence coordinate is available inside the accepted finite-section route.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_window\_readback\_determinacy}
\begin{proof}
Read the carrier rows in \autoref{def:finite-real-section-carrier}. The only stream coordinate exposed by $S$ is $W$, and the only regular-rational coordinate is $R$.

Apply \autoref{thm:finite-real-section-obligation-surface}. Its window-readback compatibility clause is the unique obligation that relates the displayed $\StreamNameUp$ window of \autoref{ch:concrete-instances-streamname-namecert} to the $\RegSeqRatUp$ readback of \autoref{ch:concrete-instances-regseqrat-namecert}.

Any alternative window, quotient stream, or host sequence coordinate would have to appear either as a carrier coordinate or as a named obligation. Neither appears in the tuple or in the obligation surface, so the accepted route reads $R$ through exactly the window determined by $q$.
\end{proof}

\begin{theorem}[Finite real section dyadic-seal factorization]
\label{thm:finite-real-section-dyadic-seal-factorization}
For an accepted $\FiniteRealSectionUp$ carrier $S=(q,W,R,D,E,H,C,P,N)$ of \autoref{def:finite-real-section-carrier}, the $\RealUp$ seal row $E$ factors through the ordered route
$$
q \to W \to R \to D \to E.
$$
Here $D$ is the $\DyadicRatCoreUp$ tolerance ledger attached to the $\RegSeqRatUp$ readback, and the route admits no seal exposure that bypasses $D$.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_dyadic\_seal\_factorization}
\begin{proof}
The carrier order in \autoref{def:finite-real-section-carrier} displays the finite request, the stream window, the regular-rational readback, the dyadic tolerance ledger, and then the Real seal. Thus $E$ is not an independent coordinate of an ambient completed Real; it is the seal row reached from the preceding displayed data.

Apply \autoref{thm:finite-real-section-obligation-surface}. Dyadic-tolerance exposure precedes $\RealUp$ seal exposure in the listed local $\NameCert_{\FiniteRealSectionUp}$ surface. The $\DyadicRatCoreUp$ chapter \autoref{ch:concrete-instances-dyadicratcore-namecert} supplies the tolerance-ledger role of $D$, and the $\RealUp$ chapter \autoref{ch:concrete-instances-real-namecert} supplies the seal-row role of $E$.

Because the accepted surface contains no second seal row and no bypass obligation, every Real-facing use of $E$ factors through the displayed ledger $D$ attached to the readback $R$.
\end{proof}

\begin{theorem}[Finite real section route consumer exactness]
\label{thm:finite-real-section-route-consumer-exactness}
Every Real- or completion-facing consumer of an accepted $\FiniteRealSectionUp$ carrier sees exactly the rows
$$
q,W,R,D,E,H,C,P,N,
$$
transported by $\hsame$, read through $\Cont$, and packaged by $\Pkg$ and $\NameCert$. Conversely, those rows assemble the accepted finite-section consumer route.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_route\_consumer\_exactness}
\begin{proof}
For the forward direction, start from \autoref{def:finite-real-section-carrier}. A consumer can project the displayed finite request, $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealUp$ seal, transport row, replay row, provenance row, and local naming row.

Apply \autoref{thm:finite-real-section-obligation-surface}. The same theorem identifies the admissible consumer surface: componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.

For the converse direction, assume precisely the nine displayed rows with the stated transport, replay, packaging, and naming support. They match the carrier coordinates and satisfy the listed local obligations, so they assemble the accepted finite-section route and expose no additional Real, completion, quotient, or host-sequence coordinate.
\end{proof}

\begin{theorem}[Finite real section non-escape]
\label{thm:finite-real-section-nonescape}
Every Real- or Completion-facing consumer of an accepted $\FiniteRealSectionUp$ packet factors through the finite route
$$
q,W,R,D,E,H,C,P,N.
$$
The consumer receives a single precision request, one $\StreamNameUp$ window, one $\RegSeqRatUp$ readback, one $\DyadicRatCoreUp$ tolerance row, one $\RealUp$ seal, and the displayed transport, replay, provenance, and local naming rows. It receives no quotient stream equality, host sequence equality, selected host limit, countable-choice selector, ambient Real completeness, or standard bridge.
\end{theorem}
\begin{proof}
Begin with \autoref{def:finite-real-section-carrier}. The only Real-facing coordinate is the seal row $E$, and it is downstream of the finite request $q$, stream window $W$, regular-rational readback $R$, and dyadic tolerance ledger $D$.

Apply \autoref{thm:finite-real-section-obligation-surface}. It forces every consumer to pass through carrier admission, classifier stability, window-readback compatibility, dyadic-tolerance exposure, seal exposure, transport, replay, provenance, and local naming before using the packet.

The excluded objects require coordinates that the carrier does not contain. The rows $H,C,P,N$ preserve and name displayed data, but they do not create quotient stream equality, host sequence equality, a selected host limit, a countable-choice selector, ambient Real completeness, or a standard bridge. Hence none of those objects can be projected from the finite-section certificate.
\end{proof}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_nonescape}

\begin{theorem}[Finite real section transport stability]
\label{thm:finite-real-section-transport-stability}
Let
$$
S=(q,W,R,D,E,H,C,P,N)
$$
and
$$
S'=(q',W',R',D',E',H',C',P',N')
$$
be accepted $\FiniteRealSectionUp$ packets. If $H$ displays componentwise $\hsame$ transport from $S$ to $S'$, then the transported packet preserves the same precision request, the same $\StreamNameUp$ window role, the same $\RegSeqRatUp$ readback role, the same $\DyadicRatCoreUp$ ledger role, the same $\RealUp$ seal role, the same $\Cont$ replay route, the same $\Pkg$ provenance, and the same local $\NameCert_{\FiniteRealSectionUp}$ route.
\end{theorem}
\begin{proof}
Project the two carrier tuples through \autoref{def:finite-real-section-carrier}. The only rows eligible for transport are the displayed request, window, readback, ledger, seal, replay, provenance, and local naming rows.

Apply \autoref{thm:finite-real-section-obligation-surface}. Its componentwise $\hsame$ clause says that $H$ transports the listed carrier coordinates and not an ambient Real object or quotient representative.

The consumer side is fixed by \autoref{thm:finite-real-section-route-consumer-exactness}: every Real- or completion-facing use reads precisely the transported finite route. Finally, \autoref{thm:finite-real-section-nonescape} excludes any target outside that route, so transport preserves the same finite-section request and its local certificate.
\end{proof}

\begin{theorem}[Finite real section refinement noncollapse]
\label{thm:finite-real-section-refinement-noncollapse}
For an accepted $\FiniteRealSectionUp$ packet $S=(q,W,R,D,E,H,C,P,N)$, a displayed refinement of the finite request through $C$ may refine the visible finite window, readback, ledger, and seal rows along the same route
$$
q \to W \to R \to D \to E.
$$
It cannot create a second stream, quotient stream equality, selected host limit, countable-choice row, ambient completeness row, or standard bridge row.
\end{theorem}
\leanchecked{BEDC.Derived.FiniteRealSectionUp.FiniteRealSection\_refinement\_noncollapse}
\begin{proof}
Read the carrier in the order $q,W,R,D,E,H,C,P,N$ from \autoref{def:finite-real-section-carrier}. The replay row $C$ is downstream support for that ordered finite request; it is not an additional source of stream, quotient, host-limit, choice, completeness, or bridge data.

Use \autoref{thm:finite-real-section-dyadic-seal-factorization}. The Real-facing seal factors through the displayed dyadic ledger, so refining the finite request can only refine rows already sitting on the route from $q$ to $E$.

It remains to rule out collapse into a larger completion surface. Apply \autoref{thm:finite-real-section-nonescape}: the excluded objects require coordinates absent from the carrier and absent from the local obligation surface. Hence displayed refinement through $C$ preserves finite visibility without creating any of those rows.
\end{proof}

\begin{theorem}[Finite real section obligation-closure package]
\label{thm:finite-real-section-obligation-closure-package}
The carrier of \autoref{def:finite-real-section-carrier}, the obligation surface of \autoref{thm:finite-real-section-obligation-surface}, window-readback determinacy of \autoref{thm:finite-real-section-window-readback-determinacy}, dyadic-seal factorization of \autoref{thm:finite-real-section-dyadic-seal-factorization}, route consumer exactness of \autoref{thm:finite-real-section-route-consumer-exactness}, non-escape of \autoref{thm:finite-real-section-nonescape}, transport stability of \autoref{thm:finite-real-section-transport-stability}, and refinement noncollapse of \autoref{thm:finite-real-section-refinement-noncollapse} are exactly the finite-section obligation set for $\FiniteRealSectionUp$ over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$.
\end{theorem}
\begin{proof}
The carrier fixes the nine-row finite section over $\BHist$. The obligation surface names the admissible local $\NameCert_{\FiniteRealSectionUp}$ rows, while window-readback determinacy and dyadic-seal factorization identify the two data dependencies that a Real-facing consumer must respect.

Route consumer exactness supplies the bidirectional packaging statement: exactly those rows are visible to a consumer and exactly those rows assemble the accepted route. Non-escape removes quotient, host-limit, choice, ambient-completeness, and bridge exits from the obligation set.

The two stability clauses close the remaining transport and refinement faces. Transport stability keeps $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support on the same finite route, and refinement noncollapse keeps displayed refinement from adding any non-finite completion row. Together these clauses exhaust the finite-section obligations named for $\FiniteRealSectionUp$.
\end{proof}

\begin{theorem}[Finite real section public bridge]
\label{thm:finite-real-section-public-bridge}
The public finite-section certificate bridges the displayed $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$ rows to the abstract $\FiniteRealSectionUp$ schema. The bridge route is exactly the carrier of \autoref{def:finite-real-section-carrier}, obligation surface of \autoref{thm:finite-real-section-obligation-surface}, route exactness of \autoref{thm:finite-real-section-route-consumer-exactness}, non-escape of \autoref{thm:finite-real-section-nonescape}, transport stability of \autoref{thm:finite-real-section-transport-stability}, refinement noncollapse of \autoref{thm:finite-real-section-refinement-noncollapse}, and TasteGate alignment recorded by the existing finite-section carrier marker.
\end{theorem}
\begin{proof}
The carrier exposes the four data rows in the required order: stream window, regular-rational readback, dyadic tolerance ledger, and Real seal. The obligation surface then names the only admissible local $\NameCert_{\FiniteRealSectionUp}$ reads over those rows.

Route consumer exactness supplies the public direction of the bridge. Every Real- or completion-facing consumer sees precisely the displayed finite-section rows together with $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local naming.

Non-escape, transport stability, and refinement noncollapse supply the boundary direction. They prevent quotient streams, host limits, ambient completeness, choice, and bridge-external rows from entering the certificate while preserving the same route under transport and displayed refinement. The TasteGate alignment keeps this public package attached to the single carrier schema rather than to a sibling real-section interface.
\end{proof}

\closureat{FiniteRealSectionUp}{matureStr}

\begin{closurestatus}{\FiniteRealSectionUp}
  \constructivestory{The finite Real section is generated from a $BHist$ packet that records a finite request, stream window, regular-rational readback, dyadic tolerance ledger, and the Real-facing seal row consumed by that route. The carrier convention does not assume a completed Real object; it reads only the finite section, transports it along $hsame$, and permits $\Cont$ extensions that preserve the same finite witness. The obligation surface names the finite section and the non-escape theorem records the boundary: a consumer that needs an infinite completion witness, quotient stream, selected host limit, or ambient Real equality has left the carrier. Thus the chapter packages a finite visible section as the whole admissible certificate.}
  \theoryclosure{\matureClosure}
  \scopeclosed{This chapter exports the finite-section public consumer surface and its compact-metric, completion, and Real-consumer cross-chapter uses, consisting of the carrier, obligation surface, route consumer exactness, non-escape theorem, transport stability, refinement noncollapse, obligation-closure package, and \leanchecked{BEDC.Derived.FiniteRealSectionUp.taste\_gate} over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, $\NameCert$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{paperBridge}
  \origin{ai}
  \notclaimed{It does not claim full Real construction, infinite-section availability, quotient-stream equality, selected host limits, or ambient completeness.}
  \upgradepath{The verification-axis step remains Lean bridge checking for the same finite-section bridge; the paper-axis scope already includes compact-metric, completion, and Real-consumer cross-chapter use.}
\end{closurestatus}
