\chapter{A Concrete Naming Certificate for $\RegistryExportSurfaceUp$}
\label{ch:concrete-instances-registry-export-surface-namecert}
\origin{ai}

The $\RegistryExportSurfaceUp$ packet realizes the export-control surface of \autoref{def:philosophy-export-control-surface} inside the auditable-generativity programme of \autoref{ch:visions-philosophy-auditable-generativity}. It sits beside the cannot-claim registry packet of \autoref{ch:concrete-instances-axiszeckendorfcannotclaim-namecert}, the verified-output boundary of \autoref{ch:concrete-instances-largemodeloutputverifier-namecert}, the focused finite ledger of \autoref{ch:concrete-instances-focused-multi-hist-ledger-namecert}, the GroundCompiler recognition surface of \autoref{ch:concrete-instances-groundcompilerrecognition-namecert}, and the NameCert audit pattern of \autoref{ch:concrete-instances-physical-namecert-audit-namecert}. Those siblings supply refusal rows, checker-facing export, focused ledger scope, machine recognition, and naming-audit discipline; this carrier binds claim registration, blocking, status, machine target, audit route, and non-smuggling rows before a registry claim may leave the philosophy package.

\begin{definition}[Registry export surface carrier]
\label{def:registry-export-surface-carrier}
A $\RegistryExportSurfaceUp$ carrier is a finite $\BHist$ packet
$$
E=(R,B,S,M,A,U,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $R$ is the registration row, recording the registry entry in which the claim is allowed to appear;
\item $B$ is the blocking row, recording the cannot-claim or refusal entry that prevents export when the claim is not licensed;
\item $S$ is the status row, recording whether the claim is exported, blocked, horizon-facing, or held as a formalization target;
\item $M$ is the machine-target row, recording the exact machine-facing consumer of the registry entry;
\item $A$ is the audit row, recording the finite verification, closure-status, or ledger route that the machine target may inspect;
\item $U$ is the non-smuggling row, recording the forbidden readings that the export must not import from prose, host semantics, model output, or hidden registry state;
\item $H$ stores componentwise $\hsame$ transport for the registration, blocking, status, machine-target, audit, non-smuggling, continuation, provenance, and local naming rows;
\item $C$ stores displayed $\Cont$ replay for registration lookup, blocking lookup, status inspection, machine-target export, audit replay, and non-smuggling refusal;
\item $P$ is the $\Pkg$ provenance over $\RegistryExportSurfaceUp$, $\AxisZeckendorfCannotClaimUp$, $\LargeModelOutputVerifierUp$, $\FocusedMultiHistLedgerUp$, $\GroundCompilerRecognitionUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\RegistryExportSurfaceUp}$ row.
\end{enumerate}
The carrier contains no coordinate for an unregistered claim, a private override of $B$, a hidden machine target, or a prose-only export route.
\end{definition}
\leandef{BEDC.Derived.RegistryExportSurfaceUp.RegistryExportSurfaceUp}

\begin{theorem}[Registry export surface NameCert obligations]
\label{thm:registry-export-surface-namecert-obligations}
For the carrier of \autoref{def:registry-export-surface-carrier}, the local $\NameCert_{\RegistryExportSurfaceUp}$ surface consists exactly of six obligation rows:
\begin{enumerate}
\item carrier admission for $E=(R,B,S,M,A,U,H,C,P,N)$;
\item registration and blocking coverage through $R$ and $B$;
\item status exactness through $S$, requiring exported, blocked, horizon-facing, and formalization-target readings to remain distinct;
\item machine-target and audit exposure through $M$ and $A$;
\item non-smuggling accountability through $U$, requiring every forbidden reading to remain visible at the export boundary;
\item transport, replay, provenance, and local naming through $H,C,P,N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the finite packet of \autoref{def:registry-export-surface-carrier}. The rows $R,B,S,M,A,U$ already separate registration, refusal, status, machine target, audit route, and forbidden readings.

Registration and blocking coverage are read first. A consumer may export a claim through $R$ or block it through $B$, but it cannot erase the blocked case by reclassifying it as an exported registry entry.

The status row $S$ then determines which registry reading is available to the machine target $M$. The audit row $A$ supplies the finite route that the target may inspect, while the non-smuggling row $U$ records the readings that remain forbidden.

Finally $H,C,P,N$ transport, replay, package, and name the same rows. Since the carrier has no further coordinate, the six obligation rows exhaust the local $\NameCert_{\RegistryExportSurfaceUp}$ surface.
\end{proof}

\begin{theorem}[Registry export surface non-escape]
\label{thm:registry-export-surface-nonescape}
Let
$$
E=(R,B,S,M,A,U,H,C,P,N)
$$
be an accepted $\RegistryExportSurfaceUp$ packet. Any public consumer that exports a registry claim must read the registration row $R$, blocking row $B$, status row $S$, machine-target row $M$, audit row $A$, non-smuggling row $U$, transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$. The export cannot be recovered from prose synthesis, model output, hidden registry state, or a machine target that bypasses the blocking row.
\end{theorem}
\begin{proof}
Use the NameCert obligations of \autoref{thm:registry-export-surface-namecert-obligations}. They place registration, blocking, status, machine-target export, audit replay, and non-smuggling accountability inside one finite packet.

If a route omits $B$, the route no longer knows whether the claim is blocked by a registry entry. If it omits $U$, the route no longer records which prose, host-semantic, model-output, or hidden-state readings are forbidden.

The rows $H,C,P,N$ bind these checks to the same displayed packet. Hence every accepted export remains inside the listed rows, and any route that bypasses them exits the $\RegistryExportSurfaceUp$ carrier rather than exporting a BEDC registry claim.
\end{proof}

\begin{theorem}[Registry export surface status exactness]
\label{thm:registry-export-surface-status-exactness}
Let
$$
E=(R,B,S,M,A,U,H,C,P,N)
$$
be an accepted $\RegistryExportSurfaceUp$ $\BHist$ packet with $\hsame$ transport $H$, $\Cont$ replay $C$, provenance package $P$, and local $\NameCert_{\RegistryExportSurfaceUp}$ row $N$. The status row $S$ keeps the exported, blocked, horizon-facing, and formalization-target readings as separate registry statuses: no $\NameCert_{\RegistryExportSurfaceUp}$ audit may identify any two of these readings while preserving the displayed registration row $R$, blocking row $B$, machine-target row $M$, audit row $A$, and non-smuggling row $U$.
\end{theorem}
\begin{proof}
Unpack the carrier of \autoref{def:registry-export-surface-carrier}. The row $S$ is the only displayed coordinate assigned to export status, and the definition lists exported, blocked, horizon-facing, and formalization-target readings as the alternatives recorded there.

Apply the NameCert obligations of \autoref{thm:registry-export-surface-namecert-obligations}. Their third row requires status exactness through $S$, and their surrounding rows keep $R,B,M,A,U,H,C,P,N$ in the same finite packet.

Finally use the non-escape theorem, \autoref{thm:registry-export-surface-nonescape}. A consumer that tries to merge two status readings must still read $B$ and $U$ through the same transport and replay rows; if it bypasses either row, it no longer exports from the $\RegistryExportSurfaceUp$ carrier. Thus the four status readings remain distinct for every accepted packet audit.
\end{proof}

\begin{theorem}[Registry export surface machine-target audit route]
\label{thm:registry-export-surface-machine-target-audit-route}
Let
$$
E=(R,B,S,M,A,U,H,C,P,N)
$$
be an accepted $\RegistryExportSurfaceUp$ $\BHist$ packet. Every machine-target export from $E$ factors through the displayed machine target $M$, audit row $A$, transport row $H$, replay row $C$, provenance package $P$, and local $\NameCert_{\RegistryExportSurfaceUp}$ row $N$, and this factorization cannot bypass the blocking row $B$.
\end{theorem}
\begin{proof}
Read the carrier in \autoref{def:registry-export-surface-carrier}. The machine-facing consumer is not an ambient parameter: it is the row $M$, and the route it may inspect is the row $A$ together with $H,C,P,N$.

The NameCert obligations of \autoref{thm:registry-export-surface-namecert-obligations} place machine-target and audit exposure in one row, and they place transport, replay, provenance, and local naming in the final row. These rows therefore describe the finite route from the machine target back to the named packet.

The blocking row is still part of the same export. By \autoref{thm:registry-export-surface-nonescape}, any public consumer exporting a registry claim must read $B$ as well as $M,A,H,C,P,N$. A purported machine target that reaches the claim without $B$ is outside the accepted carrier rather than a machine-target export from $E$.
\end{proof}

\begin{theorem}[Registry export surface non-smuggling ledger exhaustion]
\label{thm:registry-export-surface-nonsmuggling-ledger-exhaustion}
Let
$$
E=(R,B,S,M,A,U,H,C,P,N)
$$
be an accepted $\RegistryExportSurfaceUp$ $\BHist$ packet. The prose reading, host-semantic reading, model-output reading, and hidden-registry-state reading are refused by the non-smuggling row $U$ together with the displayed $\hsame$ transport $H$, $\Cont$ replay $C$, provenance package $P$, and local $\NameCert_{\RegistryExportSurfaceUp}$ row $N$; no further ledger coordinate is available for importing any of these readings into the registry export.
\end{theorem}
\begin{proof}
The carrier definition names $U$ as the row that records forbidden readings from prose, host semantics, model output, and hidden registry state. It also states that the packet contains no coordinate for a prose-only export route, hidden machine target, or private override of the blocking row.

The NameCert obligations of \autoref{thm:registry-export-surface-namecert-obligations} make this refusal visible at the export boundary. They assign non-smuggling accountability to $U$ and bind it to the transport, replay, provenance, and local naming rows $H,C,P,N$.

It remains to exclude a hidden ledger extension. Apply \autoref{thm:registry-export-surface-nonescape}: every accepted public export must read $U,H,C,P,N$ along with the registration, blocking, status, machine-target, and audit rows. Since the carrier has no additional coordinate, the listed rows exhaust the ledger route and refuse exactly the four forbidden readings named in the theorem.
\end{proof}

\begin{theorem}[Registry export surface TasteGate obligation]
\label{thm:registry-export-surface-tastegate-obligation}
The Lean follow-up for $\RegistryExportSurfaceUp$ must provide $\Nontrivial\ \RegistryExportSurfaceUp$ and $\FieldFaithful\ \RegistryExportSurfaceUp$ in $\mathsf{lean4/BEDC/Derived/RegistryExportSurfaceUp/TasteGate.lean}$, with the nontriviality witness exposing at least one accepted registration-or-blocking packet and the field-faithfulness witness preserving the distinct rows $R,B,S,M,A,U,H,C,P,N$.
\end{theorem}
\begin{proof}
The carrier in \autoref{def:registry-export-surface-carrier} is not a terminal tag: it has separate rows for registration, blocking, status, machine target, audit route, and non-smuggling accountability. A TasteGate witness must therefore exhibit a packet in which these rows are inspectable.

Field faithfulness is exactly the requirement that the classifier not collapse the rows that the NameCert obligations keep apart. In particular, $R$ cannot substitute for $B$, $M$ cannot substitute for $A$, and $U$ cannot be erased after a successful export.

Thus the Lean surface named in the theorem is the appropriate follow-up site for the same finite carrier, with nontriviality and field-faithfulness aligned to the displayed rows.
\end{proof}

\falsifiablePrediction{If the blocking row is absent, no accepted RegistryExportSurfaceUp packet exports a blocked-claim reading.}

\independenceWitness{cannotclaim, largemodeloutputverifier, focused-multi-hist-ledger, groundcompilerrecognizerflow: the cannot-claim packet records refusal rows without machine-target export, the large-model verifier records checked output without registry status coverage, the focused multi-Hist ledger records a finite focus ledger without claim blocking, and the GroundCompiler recognizer flow records machine recognition without the full registration, blocking, audit, and non-smuggling packet. None is bijective to $\RegistryExportSurfaceUp$.}

\closureat{RegistryExportSurfaceUp}{seedStr}
\closureat{RegistryExportSurfaceUp}{obligationStr}
\closureat{RegistryExportSurfaceUp}{scopedStr}

\begin{closurestatus}{\RegistryExportSurfaceUp}
  \constructivestory{A $\RegistryExportSurfaceUp$ packet is generated from registration, blocking, status, machine-target, audit, non-smuggling, transport, replay, provenance, and local naming rows.}
  \leanchecked{BEDC.Derived.RegistryExportSurfaceUp.taste\_gate}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The closed scope consists of the explicit rows $R,B,S,M,A,U,H,C,P,N$ over $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, together with the cannot-claim, large-model-output verifier, focused multi-Hist ledger, GroundCompiler recognition, and physical NameCert audit sibling export-control anchors.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, hidden registry state, prose-only export, or machine targets that bypass blocking.}
  \upgradepath{Lean closure requires checked registration, blocking, status, machine-target, audit, non-smuggling, transport, replay, provenance, and local naming rows.}
\end{closurestatus}
