\chapter{A Concrete Naming Certificate for $\RegularCauchyDiagonalUp$}
\label{ch:concrete-instances-regularcauchydiagonal-namecert}
\origin{human}

The $\RegularCauchyDiagonalUp$ packet names the stationary and finite-window diagonal data used by the real-completeness construction before it is repacked into the broader $\RealDiagonalCompletionUp$ surface. Its carrier is deliberately smaller than a completion theorem: it records the inspected regular Cauchy rows, the diagonal selector, the stationary rational rows, and the local naming-certificate provenance through $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The diagonal packet consumes the $\StreamNameUp$ window carrier of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, and exports to the $\RealDiagonalCompletionUp$ consumer of \autoref{ch:concrete-instances-real-diagonal-completion-namecert}.

\begin{definition}[Regular Cauchy diagonal source]
\label{def:regular-cauchy-diagonal-source}
A $\RegularCauchyDiagonalUp$ source row is a finite $\mathsf{BHist}$ packet
$$
D=(Q,S,R,L,W,P,N)
$$
whose displayed coordinates are as follows:
\begin{enumerate}
\item $Q$ is the visible $\RatUp$ seed row used for stationary rational inputs;
\item $S$ is the $\StreamNameUp$ row naming the stream windows read by the diagonal selector;
\item $R$ is the $\RegSeqRatUp$ row naming the regular rational sequence selected at the requested diagonal precision;
\item $L$ is the $\RealUp$ seal row receiving the selected diagonal representative;
\item $W$ is the finite list of requested diagonal windows and their $\Cont$ routes through the inspected regular Cauchy family;
\item $P$ is the $\Pkg$ row naming the $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and local certificate dependencies;
\item $N$ is the local $\NameCert_{\RegularCauchyDiagonalUp}$ provenance row.
\end{enumerate}
The source row contains no quotient of regular streams, no selected host limit, and no ambient completeness field.
\end{definition}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalTasteGate\_single\_carrier\_alignment}

\begin{definition}[Regular Cauchy diagonal carrier]
\label{def:regular-cauchy-diagonal-carrier}
The carrier of $\RegularCauchyDiagonalUp$ consists of the source rows of \autoref{def:regular-cauchy-diagonal-source} whose diagonal windows are all read from displayed $\RegSeqRatUp$ rows and whose stationary rational rows factor through the same $\RatUp$ seed, the same $\StreamNameUp$ constant-window witness, and the same $\RealUp$ seal row. The classifier relates two carrier rows exactly when their visible rational seeds, stream windows, regular-sequence reads, real-seal rows, and package provenance are transported componentwise by the displayed $\hsame$ comparisons and $\Cont$ routes.
\end{definition}
\leandef{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier}

\begin{theorem}[Regular Cauchy diagonal window coverage]
\label{thm:regular-cauchy-diagonal-window-coverage}
Every consumer read of an accepted $\RegularCauchyDiagonalUp$ carrier factors through one displayed diagonal window, one $\StreamNameUp$ window row, one $\RegSeqRatUp$ readback row, the associated $\RatUp$ seed evidence for stationary rational rows, and the visible $\Pkg$ and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_window\_coverage}
\begin{proof}
Project the accepted carrier through \autoref{def:regular-cauchy-diagonal-carrier}. The only consumer-facing coordinates are the diagonal-window list, the stream-window row, the regular rational readback, the real-seal row, and the local provenance rows.

For a requested precision, the diagonal selector chooses a displayed member of the regular Cauchy family and a displayed window inside that member. The $\Cont$ route in the source packet records that this window is one of the finite rows already named by the $\StreamNameUp$ schedule.

The selected value is then read through the $\RegSeqRatUp$ row and, in the stationary case, through the same $\RatUp$ seed row. Repacking these visible rows with $P$ and $N$ gives the claimed factorization, and there is no additional carrier coordinate from which a host limit or quotient equality could be read.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal stationary compatibility]
\label{thm:regular-cauchy-diagonal-stationary-compatibility}
If a $\RegularCauchyDiagonalUp$ carrier row is generated by a stationary rational seed $Q:\RatUp$, then every diagonal window reads the same rational seed through the constant $\StreamNameUp$ row, and the resulting $\RealUp$ seal is classified with the constant rational embedding of $Q$.
\end{theorem}
\begin{proof}
In the stationary packet, every inspected member of the regular Cauchy family is the same regular rational row. The diagonal selector may vary the requested window, but the stream row is constant and each selected observation is transported by the same displayed $\hsame$ and $\Cont$ witnesses.

Thus the $\RegSeqRatUp$ readback row carries the seed $Q$ at every diagonal window. The $\RealUp$ seal coordinate is attached to exactly those readbacks, so the constant rational embedding receives the same rational seed and the same local provenance.

The classifier of \autoref{def:regular-cauchy-diagonal-carrier} compares only the displayed seed, window, readback, seal, and package rows. It therefore identifies the stationary diagonal carrier with the constant rational $\RealUp$ embedding of $Q$.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_stationary\_compatibility}

\begin{theorem}[Regular Cauchy diagonal NameCert obligations]
\label{thm:regular-cauchy-diagonal-namecert-obligations}
The local $\NameCert_{\RegularCauchyDiagonalUp}$ obligation surface consists of carrier habitation, componentwise classifier transport through $\hsame$ and $\Cont$, diagonal-window coverage, stationary rational compatibility, and ledger non-escape over $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\mathsf{BHist}$, $\Pkg$, and $\NameCert$.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_namecert\_obligations}
\begin{proof}
Carrier habitation is the packaging operation of \autoref{def:regular-cauchy-diagonal-carrier}: the source row supplies the rational seed, stream windows, regular-sequence readbacks, real seal, finite diagonal-window routes, and provenance rows.

Classifier transport is componentwise. Each accepted replacement is an $\hsame$ comparison of one displayed row or a $\Cont$ route identifying where that row is read inside the finite diagonal packet, so the transported packet remains within the same carrier definition.

Window coverage is exactly \autoref{thm:regular-cauchy-diagonal-window-coverage}, and stationary rational compatibility is exactly \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. The ledger non-escape claim follows by inspecting the listed source coordinates: none is a quotient carrier, host-limit selector, ambient completeness theorem, or hidden real endpoint.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_semantic\_name\_certificate}

\begin{theorem}[Regular Cauchy diagonal zero seed]
\label{thm:regular-cauchy-diagonal-zero-seed}
For the source row $D=(Q,S,R,L,W,P,N)$ of \autoref{def:regular-cauchy-diagonal-source}, the stationary rational seed with $Q$ the zero $\RatUp$ row, $S$ the constant $\StreamNameUp$ window row, and $R$ the constant $\RegSeqRatUp$ readback inhabits the $\RegularCauchyDiagonalUp$ carrier. Its $\RealUp$ seal row $L$, finite window ledger $W$, package row $P$, and local $\NameCert$ row $N$ are all displayed finite rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_zero\_seed}
\begin{proof}
Start with the stationary rational seed. The zero $\RatUp$ row supplies the same displayed rational observation at every requested diagonal precision, and the constant $\StreamNameUp$ row supplies the same finite window witness for each read.

The $\RegSeqRatUp$ readback is therefore the constant regular rational row. By \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}, the resulting $\RealUp$ seal is classified with the constant rational embedding of the same seed.

Finally package the constant window routes with $P$ and $N$. The carrier definition in \autoref{def:regular-cauchy-diagonal-carrier} requires no quotient stream, selected host limit, or ambient completeness field, so these displayed rows inhabit the diagonal carrier.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal selector stability]
\label{thm:regular-cauchy-diagonal-selector-stability}
Let $D=(Q,S,R,L,W,P,N)$ be an accepted $\RegularCauchyDiagonalUp$ source row. Transporting $Q$, $S$, $R$, $L$, $W$, $P$, and $N$ componentwise by the displayed $\hsame$ comparisons and $\Cont$ routes preserves the diagonal selector classifier through the $\RatUp$, $\StreamNameUp$, and $\RegSeqRatUp$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_selector\_stability}
\begin{proof}
Project the classifier from \autoref{def:regular-cauchy-diagonal-carrier}. It compares only visible rational seeds, stream windows, regular-sequence readbacks, real-seal rows, finite diagonal-window routes, and provenance.

The selector uses the window list $W$ to choose a displayed window inside the inspected regular Cauchy family. Componentwise $\hsame$ comparisons and $\Cont$ routes move exactly those displayed windows and readback rows, so the selected diagonal row remains inside the same finite packet.

Apply \autoref{thm:regular-cauchy-diagonal-window-coverage} for the consumer-facing route and \autoref{thm:regular-cauchy-diagonal-namecert-obligations} for the local certificate surface. Together they show that the transported packet preserves the selector classifier without adding quotient streams, host limits, or ambient completeness data.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal RealUp seal handoff]
\label{thm:regular-cauchy-diagonal-real-seal-handoff}
For every accepted source row $D=(Q,S,R,L,W,P,N)$, the $\RealUp$ seal row $L$ is reached only through the displayed $\RatUp$ seed row, $\StreamNameUp$ window row, and $\RegSeqRatUp$ diagonal readback row. This handoff is the $\NameCert_{\RegularCauchyDiagonalUp}$ seal-facing route consumed by downstream $\RealDiagonalCompletionUp$ and $\RealCauchyCompletionUp$ packets.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_real\_seal\_handoff}
\begin{proof}
Read a consumer request through \autoref{thm:regular-cauchy-diagonal-window-coverage}. The request first selects a displayed diagonal window, then reads the corresponding $\StreamNameUp$ window row and $\RegSeqRatUp$ regular rational row.

In the stationary case, \autoref{thm:regular-cauchy-diagonal-stationary-compatibility} identifies the same route with the $\RatUp$ seed and its constant rational $\RealUp$ embedding. In the general accepted packet, the same coordinates are carried by $Q$, $S$, $R$, and $W$.

The obligation surface of \autoref{thm:regular-cauchy-diagonal-namecert-obligations} records the seal row $L$ only after those displayed rows and the provenance rows $P$ and $N$. Hence the seal handoff is finite and visible, and no host limit, quotient stream, or ambient completeness theorem is exported to downstream completion packets.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal completion consumer bridge]
\label{thm:regular-cauchy-diagonal-completion-consumer-bridge}
Every downstream $\RealDiagonalCompletionUp$ or $\RealCauchyCompletionUp$ consumer of an accepted $\RegularCauchyDiagonalUp$ packet factors through the displayed tuple $D=(Q,S,R,L,W,P,N)$, the diagonal-window coverage route of \autoref{thm:regular-cauchy-diagonal-window-coverage}, and the $\RealUp$ seal handoff of \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. The consumer receives no quotient stream, selected host limit, or ambient completeness row from the diagonal packet.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:regular-cauchy-diagonal-source} and \autoref{def:regular-cauchy-diagonal-carrier}. The only exported coordinates are the rational seed $Q$, stream row $S$, regular readback $R$, seal row $L$, finite window ledger $W$, package row $P$, and local certificate row $N$.

Apply \autoref{thm:regular-cauchy-diagonal-window-coverage} to route each completion read through a displayed diagonal window and its $\StreamNameUp$ and $\RegSeqRatUp$ rows. Then apply \autoref{thm:regular-cauchy-diagonal-real-seal-handoff} to reach $L$ through exactly those displayed rows.

The carrier definition has no coordinate for a quotient of streams, a chosen external limit, or an ambient completeness witness. Thus any completion consumer using the accepted packet can only consume the displayed tuple and the two named routes.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_completion\_consumer\_bridge}

\begin{theorem}[Regular Cauchy diagonal stationary seal exactness]
\label{thm:regular-cauchy-diagonal-stationary-seal-exactness}
In the stationary rational case, the completion-facing seal route of an accepted $\RegularCauchyDiagonalUp$ packet is exactly the constant route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$ supplied by \autoref{thm:regular-cauchy-diagonal-stationary-compatibility} and \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}.
\end{theorem}
\begin{proof}
Start with a stationary source row $D=(Q,S,R,L,W,P,N)$. By \autoref{def:regular-cauchy-diagonal-carrier}, the stream row $S$ is the constant-window row over the same rational seed $Q$, and $R$ is the displayed regular rational readback selected from that constant stream.

Apply \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. Every diagonal window reads the same $\RatUp$ seed through the constant $\StreamNameUp$ row and the associated $\RegSeqRatUp$ readback.

Apply \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. The seal row $L$ is reached only after those displayed rows, so the route to $\RealUp$ is precisely the constant stationary route and not a route through any host completion witness.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_stationary\_seal\_exactness}

\begin{theorem}[Regular Cauchy diagonal bridge obligation package]
\label{thm:regular-cauchy-diagonal-bridge-obligation-package}
The bridge-facing obligation package for $\RegularCauchyDiagonalUp$ consists of five finite obligations: carrier habitation, selector stability, diagonal-window coverage, stationary seal exactness, and completion-consumer routing. Together these are the obligations needed to pass from the public diagonal packet to the bridge-facing completion surface.
\end{theorem}
\begin{proof}
Carrier habitation is obtained by projecting \autoref{def:regular-cauchy-diagonal-source} into \autoref{def:regular-cauchy-diagonal-carrier}. The source row supplies $Q$, $S$, $R$, $L$, $W$, $P$, and $N$, and the carrier condition records that the selected diagonal reads stay inside those displayed rows.

Selector stability is \autoref{thm:regular-cauchy-diagonal-selector-stability}, and diagonal-window coverage is \autoref{thm:regular-cauchy-diagonal-window-coverage}. These two obligations show that transported packets preserve the visible selector and that every consumer read has a named finite window.

Stationary seal exactness is \autoref{thm:regular-cauchy-diagonal-stationary-seal-exactness}. Completion-consumer routing is \autoref{thm:regular-cauchy-diagonal-completion-consumer-bridge}. Repacking these five projections gives the bridge-facing package, while the source and carrier definitions exclude quotient streams, selected host limits, and ambient completeness rows.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_bridge\_obligation\_package}

\begin{theorem}[Regular Cauchy diagonal standard bridge source]
\label{thm:regular-cauchy-diagonal-standard-bridge-source}
For every accepted source row $D=(Q,S,R,L,W,P,N)$, the $\RegularCauchyDiagonalUp$ bridge source is the finite tuple consisting of the $\RatUp$ seed $Q$, the $\StreamNameUp$ window row $S$, the $\RegSeqRatUp$ diagonal readback $R$, the $\RealUp$ seal $L$, the diagonal-window ledger $W$, the package row $P$, and the local $\NameCert$ row $N$, together with the displayed $\mathsf{BHist}$ carrier, $\hsame$ classifier, $\Cont$ routes, selector-stability proof, window-coverage proof, stationary-compatibility proof, and seal handoff to $\RealUp$. This tuple is a standard BEDC bridge source from the diagonal selector package to the real-completion consumer surface.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:regular-cauchy-diagonal-source} and \autoref{def:regular-cauchy-diagonal-carrier}. These definitions supply exactly the visible carrier coordinates $Q$, $S$, $R$, $L$, $W$, $P$, and $N$, and they identify the classifier as componentwise $\hsame$ transport with displayed $\Cont$ routes.

The consumer-facing coverage row is \autoref{thm:regular-cauchy-diagonal-window-coverage}. Selector stability is \autoref{thm:regular-cauchy-diagonal-selector-stability}, and stationary rational compatibility is \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. These three rows keep every selected diagonal read inside the displayed $\RatUp$, $\StreamNameUp$, and $\RegSeqRatUp$ surface.

Finally apply the local NameCert obligation surface of \autoref{thm:regular-cauchy-diagonal-namecert-obligations} and the $\RealUp$ seal handoff of \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. Repacking these rows gives the standard bridge source; no additional host completion object is needed to form the source.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_standard\_bridge\_source}

\begin{theorem}[Regular Cauchy diagonal bridge readback exactness]
\label{thm:regular-cauchy-diagonal-bridge-readback-exactness}
Reading the $\RegularCauchyDiagonalUp$ bridge source of \autoref{thm:regular-cauchy-diagonal-standard-bridge-source} back through its public surface recovers exactly the displayed tuple $D=(Q,S,R,L,W,P,N)$. The readback preserves the selector classifier because the only inspected rows are the $\RatUp$ seed, $\StreamNameUp$ window row, $\RegSeqRatUp$ diagonal readback, $\RealUp$ seal, finite window ledger, package provenance, and local $\NameCert$ provenance transported componentwise by $\hsame$ and $\Cont$.
\end{theorem}
\begin{proof}
Read the bridge source by projecting its carrier coordinate. By \autoref{def:regular-cauchy-diagonal-source}, the carrier contains the seven displayed coordinates $Q$, $S$, $R$, $L$, $W$, $P$, and $N$ and no further completion coordinate.

The bridge readback route is the same route used for diagonal-window coverage. Apply \autoref{thm:regular-cauchy-diagonal-window-coverage} to identify the selected window and the matching $\StreamNameUp$ and $\RegSeqRatUp$ rows, then apply \autoref{thm:regular-cauchy-diagonal-real-seal-handoff} to identify the exported seal row as $L$.

It remains to check the selector classifier. This is exactly \autoref{thm:regular-cauchy-diagonal-selector-stability}: componentwise $\hsame$ and $\Cont$ transport preserves the selected diagonal row and hence preserves the public readback tuple.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_bridge\_readback\_exactness}

\begin{theorem}[Regular Cauchy diagonal bridge non-escape]
\label{thm:regular-cauchy-diagonal-bridge-non-escape}
The $\RegularCauchyDiagonalUp$ standard bridge source exports no quotient stream, no selected host limit, no ambient completeness theorem, and no host equality. Every bridge consumer read factors through the displayed tuple $D=(Q,S,R,L,W,P,N)$, the finite window ledger, the $\RatUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ rows, and the local $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_bridge\_non\_escape}
\begin{proof}
Inspect the source coordinates in \autoref{def:regular-cauchy-diagonal-source}. The tuple lists rational seed data, stream-window data, regular rational readback data, one real-seal row, finite windows, package provenance, and local certificate provenance.

The carrier definition in \autoref{def:regular-cauchy-diagonal-carrier} adds only the displayed acceptance and classifier conditions. It does not add a quotient stream, a chosen host limit, an ambient completeness theorem, or host equality.

The bridge source of \autoref{thm:regular-cauchy-diagonal-standard-bridge-source} is assembled from this same carrier together with window coverage, selector stability, stationary compatibility, NameCert obligations, and the RealUp seal handoff. Therefore every bridge read remains inside those named rows, and the listed host-level objects cannot be exported by the bridge.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal selector-window functoriality]
\label{thm:regular-cauchy-diagonal-selector-window-functoriality}
Let $D=(Q,S,R,L,W,P,N)$ be an accepted $\RegularCauchyDiagonalUp$ source row. If the displayed $\hsame$ comparisons and $\Cont$ routes transport the visible carrier rows of $D$ to another accepted carrier row, then the diagonal selector transports the same finite $W$ window route through the $\RatUp$, $\StreamNameUp$, and $\RegSeqRatUp$ coordinates. In particular, selector transport preserves the chosen window route and does not introduce a second selector outside the displayed finite ledger.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_selector\_window\_functoriality}
\begin{proof}
Project the transport data through \autoref{def:regular-cauchy-diagonal-carrier}. The classifier compares only the displayed rational seed, stream-window row, regular readback, real-seal row, finite window ledger, and provenance rows, all carried by $\hsame$ or $\Cont$.

Apply \autoref{thm:regular-cauchy-diagonal-selector-stability} to the transported carrier row. The selector still reads a member of the same finite ledger $W$, and \autoref{thm:regular-cauchy-diagonal-window-coverage} identifies the matching $\StreamNameUp$ window and $\RegSeqRatUp$ readback.

The bridge source of \autoref{thm:regular-cauchy-diagonal-standard-bridge-source} uses exactly these rows as its selector-facing input. Therefore the transported selector route is the displayed finite route, not a host-level re-selection or a route through an unlisted completion object.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal stationary-family exhaustion]
\label{thm:regular-cauchy-diagonal-stationary-family-exhaustion}
Every stationary rational diagonal packet accepted by $\RegularCauchyDiagonalUp$ is exhausted by the displayed route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$. Equivalently, the packet has no stationary-family read outside the rational seed $Q$, the constant stream row $S$, the regular rational readback $R$, and the seal row $L$ of its source tuple $D=(Q,S,R,L,W,P,N)$.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_stationary\_family\_exhaustion}
\begin{proof}
Start with a stationary accepted carrier. By \autoref{def:regular-cauchy-diagonal-carrier}, the stationary rows factor through the same $\RatUp$ seed, the same constant $\StreamNameUp$ witness, and the same $\RealUp$ seal row.

Apply \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. Each diagonal window reads the same rational seed through the constant stream row and the associated $\RegSeqRatUp$ readback. Then apply \autoref{thm:regular-cauchy-diagonal-stationary-seal-exactness} to identify the completion-facing seal route with the displayed chain $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$.

Finally use \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}. Since the bridge exports no quotient stream, host limit, ambient completeness theorem, or host equality, there is no remaining stationary-family coordinate outside $Q$, $S$, $R$, and $L$.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal bridge route determinacy]
\label{thm:regular-cauchy-diagonal-bridge-route-determinacy}
For the standard $\RegularCauchyDiagonalUp$ bridge source, bridge readback has exactly the displayed route through $D=(Q,S,R,L,W,P,N)$. Any bridge consumer read that recovers the public surface factors through the same source tuple, the same finite window ledger, and the same local $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance; there is no second bridge route outside $D$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:regular-cauchy-diagonal-standard-bridge-source}. The bridge source is built from the seven displayed coordinates, the carrier classifier, the finite window route, selector stability, stationary compatibility, NameCert obligations, and the $\RealUp$ seal handoff.

Read the source back through \autoref{thm:regular-cauchy-diagonal-bridge-readback-exactness}. The public readback recovers the same tuple $D=(Q,S,R,L,W,P,N)$ and preserves the selector classifier by componentwise $\hsame$ and $\Cont$ transport.

It remains to exclude competing routes. This is exactly the non-escape content of \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}: every bridge consumer read remains inside the displayed tuple, finite ledger, BEDC rows, and local provenance. Hence bridge readback is determined by $D$.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_bridge\_route\_determinacy}

\begin{theorem}[Regular Cauchy diagonal mature consumer exhaustion]
\label{thm:regular-cauchy-diagonal-mature-consumer-exhaustion}
Every $\RealDiagonalCompletionUp$ or $\RealCauchyCompletionUp$ consumer read of an accepted $\RegularCauchyDiagonalUp$ packet factors through the displayed tuple $D=(Q,S,R,L,W,P,N)$, the finite window ledger, the diagonal-window coverage route of \autoref{thm:regular-cauchy-diagonal-window-coverage}, the seal handoff of \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}, and the bridge route determinacy of \autoref{thm:regular-cauchy-diagonal-bridge-route-determinacy}. The consumer receives no quotient stream, selected host limit, ambient completeness row, or host equality from the diagonal packet.
\end{theorem}
\begin{proof}
Start with an accepted diagonal packet and project its carrier through \autoref{def:regular-cauchy-diagonal-carrier}. The available rows are the rational seed, stream-window row, regular rational readback, real-seal row, finite window ledger, package provenance, and local certificate provenance.

Apply \autoref{thm:regular-cauchy-diagonal-window-coverage} to identify the visible finite window ledger, and apply \autoref{thm:regular-cauchy-diagonal-real-seal-handoff} to identify the $\RealUp$ seal read by downstream completion packets.

The remaining possible ambiguity is the bridge route by which the consumer reads the packet. \autoref{thm:regular-cauchy-diagonal-bridge-route-determinacy} identifies that route with the same displayed tuple $D=(Q,S,R,L,W,P,N)$, and \autoref{thm:regular-cauchy-diagonal-bridge-non-escape} excludes quotient streams, selected host limits, ambient completeness rows, and host equality.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_mature\_consumer\_exhaustion}

\begin{theorem}[Regular Cauchy diagonal real-completion handoff]
\label{thm:regular-cauchy-diagonal-real-completion-handoff}
The displayed route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$ is the completion-facing handoff from an accepted $\RegularCauchyDiagonalUp$ packet into the current $\RealUp$ and completion phase boundary. The handoff is determined by stationary compatibility, stationary-family exhaustion, and bridge non-escape, and it introduces no completion object beyond the displayed seal row $L$.
\end{theorem}
\begin{proof}
Begin with the stationary route supplied by \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. It reads the same rational seed through the constant $\StreamNameUp$ row and the associated $\RegSeqRatUp$ diagonal readback.

Apply \autoref{thm:regular-cauchy-diagonal-stationary-family-exhaustion}. This shows that the stationary packet has no family read outside $Q$, $S$, $R$, and the seal row $L$ of $D=(Q,S,R,L,W,P,N)$.

Finally apply \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}. Since the bridge exports no quotient stream, selected host limit, ambient completeness theorem, or host equality, the only completion-facing object exposed by the route is the displayed $\RealUp$ seal row.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_real\_completion\_handoff}

\begin{theorem}[Regular Cauchy diagonal mature closure certificate]
\label{thm:regular-cauchy-diagonal-mature-closure-certificate}
The $\RegularCauchyDiagonalUp$ paper surface has a mature consumer package consisting of carrier habitation, selector stability, window coverage, stationary compatibility, seal handoff, the standard bridge source, readback exactness, bridge non-escape, mature consumer exhaustion, and real-completion handoff. Consequently every accepted diagonal selector packet consumed at the current $\RealUp$ completion boundary is accounted for by the displayed tuple $D=(Q,S,R,L,W,P,N)$ and its finite ledger.
\end{theorem}
\begin{proof}
Collect the carrier and local certificate clauses first. Carrier habitation is supplied by the local obligation package of \autoref{thm:regular-cauchy-diagonal-namecert-obligations}, selector stability by \autoref{thm:regular-cauchy-diagonal-selector-stability}, window coverage by \autoref{thm:regular-cauchy-diagonal-window-coverage}, stationary compatibility by \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}, and seal handoff by \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}.

Next collect the bridge-facing clauses. The standard source is \autoref{thm:regular-cauchy-diagonal-standard-bridge-source}, readback exactness is \autoref{thm:regular-cauchy-diagonal-bridge-readback-exactness}, and non-escape is \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}.

It remains to connect the bridge surface to the completion consumers. This is exactly the mature consumer exhaustion of \autoref{thm:regular-cauchy-diagonal-mature-consumer-exhaustion} together with the real-completion handoff of \autoref{thm:regular-cauchy-diagonal-real-completion-handoff}. These clauses package the accepted packet as the displayed tuple and finite ledger consumed at the current $\RealUp$ completion boundary.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_mature\_closure\_certificate}

\begin{theorem}[Regular Cauchy diagonal source stability obligation]
\label{thm:regular-cauchy-diagonal-source-stability-obligation}
Let $D=(Q,S,R,L,W,P,N)$ be an accepted $\RegularCauchyDiagonalUp$ source row. If the displayed $\hsame$ comparisons and $\Cont$ routes transport $Q$, $S$, $R$, $L$, $W$, $P$, and $N$ to another accepted source row, then carrier admission, the diagonal selector classifier, the stationary rational route, and the $\RealUp$ seal route are transported through the same finite tuple. No transported source read leaves the rows named in $D$.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_source\_stability\_obligation}
\begin{proof}
Project $D$ through \autoref{def:regular-cauchy-diagonal-source} and \autoref{def:regular-cauchy-diagonal-carrier}. The classifier compares only the rational seed, stream-window row, regular readback, seal row, finite window ledger, package row, and local naming row.

Apply \autoref{thm:regular-cauchy-diagonal-selector-stability}. The displayed $\hsame$ comparisons and $\Cont$ routes preserve the selector classifier through the $\RatUp$, $\StreamNameUp$, and $\RegSeqRatUp$ coordinates.

For the completion-facing read, apply \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. The seal row $L$ is reached only after the transported source rows, so source stability is exactly the finite transport of $D$.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal window ledger exactness]
\label{thm:regular-cauchy-diagonal-window-ledger-exactness}
For every accepted $\RegularCauchyDiagonalUp$ source row $D=(Q,S,R,L,W,P,N)$, every diagonal consumer window is exactly one of the finite entries of the displayed ledger $W$. The entry names its $\StreamNameUp$ window, the matching $\RegSeqRatUp$ readback, the stationary $\RatUp$ seed route when present, and the $\Cont$ route by which the $\RealUp$ seal can later be read.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_window\_ledger\_exactness}
\begin{proof}
Start with a consumer window request. By \autoref{thm:regular-cauchy-diagonal-window-coverage}, the request factors through a displayed diagonal window, a stream-window row, a regular rational readback row, and the local provenance rows.

The carrier definition records no unlisted window source. Therefore the displayed window reached by the consumer is an entry of $W$, with the associated $\Cont$ route and readback rows already attached to that entry.

In the stationary case, \autoref{thm:regular-cauchy-diagonal-stationary-compatibility} identifies the same entry with the constant $\RatUp$ seed route. The seal-facing route is then supplied by \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}, so the ledger entry is exact for downstream consumers.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal NameCert consumer surface]
\label{thm:regular-cauchy-diagonal-namecert-consumer-surface}
The public $\NameCert_{\RegularCauchyDiagonalUp}$ consumer surface for $D=(Q,S,R,L,W,P,N)$ consists exactly of carrier admission, source stability, finite window-ledger exactness, stationary rational compatibility, selector stability, and the $\RealUp$ seal handoff. Each clause is read through $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and the local $\NameCert$ row already displayed by the source tuple.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_namecert\_consumer\_surface}
\begin{proof}
First collect the local certificate rows. Carrier admission and local naming obligations are \autoref{thm:regular-cauchy-diagonal-namecert-obligations}; source stability is \autoref{thm:regular-cauchy-diagonal-source-stability-obligation}.

Next collect the selector-facing rows. Window-ledger exactness is \autoref{thm:regular-cauchy-diagonal-window-ledger-exactness}, stationary rational compatibility is \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}, and selector stability is \autoref{thm:regular-cauchy-diagonal-selector-stability}.

Finally attach the seal-facing read with \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. These rows are all projections of the finite source tuple and its displayed transport routes, so the consumer surface has no quotient stream, selected host limit, ambient completeness theorem, or host equality.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal real-completion handoff package]
\label{thm:regular-cauchy-diagonal-real-completion-handoff-package}
Every $\RealCauchyCompletionUp$ or $\RealDiagonalCompletionUp$ consumer of an accepted $\RegularCauchyDiagonalUp$ source row receives the completion handoff through the tuple $D=(Q,S,R,L,W,P,N)$, the exact finite window ledger $W$, the $\RegSeqRatUp$ readback row $R$, and the $\RealUp$ seal row $L$. The handoff packages only the visible diagonal route and does not supply quotient streams, selected host limits, host equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_real\_completion\_handoff\_package}
\begin{proof}
Begin with the completion-consumer bridge of \autoref{thm:regular-cauchy-diagonal-completion-consumer-bridge}. It routes every $\RealDiagonalCompletionUp$ or $\RealCauchyCompletionUp$ request through the displayed source tuple, the window coverage row, and the seal handoff.

Replace the coverage row by the exact ledger statement \autoref{thm:regular-cauchy-diagonal-window-ledger-exactness}. This identifies each requested window with an entry of $W$ and fixes the associated $\StreamNameUp$ and $\RegSeqRatUp$ reads.

Then apply \autoref{thm:regular-cauchy-diagonal-real-completion-handoff}. The completion-facing object is the displayed $\RealUp$ seal row $L$, reached through the finite route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$ where the stationary route applies.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal downstream-unblock package]
\label{thm:regular-cauchy-diagonal-downstream-unblock-package}
The $\RegularCauchyDiagonalUp$ downstream package for the real-completion diagonal route is the composition of source stability, window-ledger exactness, the NameCert consumer surface, and the real-completion handoff package. Consequently every downstream $\RealCauchyCompletionUp$ or $\RealDiagonalCompletionUp$ read is accounted for by the displayed tuple $D=(Q,S,R,L,W,P,N)$, its finite ledger $W$, and the local $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{theorem}
\begin{proof}
First apply \autoref{thm:regular-cauchy-diagonal-source-stability-obligation}. This fixes the transport spine of the source tuple under the displayed $\hsame$ comparisons and $\Cont$ routes.

Next apply \autoref{thm:regular-cauchy-diagonal-window-ledger-exactness}. Every consumer window is one of the finite entries of $W$, with its stream-window route, regular readback, and seal-facing continuation already named.

The public certificate surface is then \autoref{thm:regular-cauchy-diagonal-namecert-consumer-surface}. The real-completion read is \autoref{thm:regular-cauchy-diagonal-real-completion-handoff-package}. Composing these rows gives the downstream package and excludes all non-displayed completion objects.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_downstream\_unblock\_package}

\begin{theorem}[Regular Cauchy diagonal root source determinacy]
\label{thm:regular-cauchy-diagonal-root-source-determinacy}
For an accepted $\RegularCauchyDiagonalUp$ root packet, the concrete source tuple $D=(Q,S,R,L,W,P,N)$ is determined as a displayed $\mathsf{BHist}$ row by the stationary $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$ route, the componentwise $\hsame$ comparisons, the displayed $\Cont$ routes, the package row $\Pkg$, and the local $\NameCert$ row. No second source for the same root packet can change $Q$, $S$, $R$, $L$, $W$, $P$, or $N$ without changing one of those displayed rows.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_root\_source\_determinacy}
\begin{proof}
Project the root packet through \autoref{def:regular-cauchy-diagonal-source} and \autoref{def:regular-cauchy-diagonal-carrier}. The carrier exposes exactly the seven rows $Q$, $S$, $R$, $L$, $W$, $P$, and $N$ inside the displayed $\mathsf{BHist}$ packet.

The source-stability row of \autoref{thm:regular-cauchy-diagonal-source-stability-obligation} identifies transport of the tuple by the recorded $\hsame$ and $\Cont$ data. The stationary compatibility row of \autoref{thm:regular-cauchy-diagonal-stationary-compatibility} fixes the route from $\RatUp$ through $\StreamNameUp$ and $\RegSeqRatUp$ to the same $\RealUp$ seal.

Thus any competing root readback must agree on the carrier rows and on the $\Pkg$ and $\NameCert$ provenance. There is no hidden completion coordinate through which a different source tuple could be substituted.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal root selector totality]
\label{thm:regular-cauchy-diagonal-root-selector-totality}
For every accepted root tuple $D=(Q,S,R,L,W,P,N)$ of $\RegularCauchyDiagonalUp$ and every classifier-facing downstream request, the selector has a displayed finite response in the $\mathsf{BHist}$ ledger $W$. The response follows the route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$ and carries only the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data attached to $D$.
\end{theorem}
\begin{proof}
Begin with a classifier-facing request and read the accepted packet through the carrier definition. The available selector data is the finite ledger $W$ together with the stream row $S$, regular readback row $R$, seal row $L$, package row $P$, and naming row $N$.

Apply \autoref{thm:regular-cauchy-diagonal-window-coverage}. It routes the request to a displayed diagonal window, the matching $\StreamNameUp$ row, and the matching $\RegSeqRatUp$ readback.

The selector-stability theorem \autoref{thm:regular-cauchy-diagonal-selector-stability} transports this response across the recorded $\hsame$ and $\Cont$ witnesses. The real-seal handoff of \autoref{thm:regular-cauchy-diagonal-real-seal-handoff} then identifies the response as the same $\RealUp$ seal row.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_root\_selector\_totality}

\begin{theorem}[Regular Cauchy diagonal root window-ledger exactness]
\label{thm:regular-cauchy-diagonal-root-window-ledger-exactness}
For a root packet with source tuple $D=(Q,S,R,L,W,P,N)$, every window read used by the Real and Completion handoff is exactly one displayed entry of the finite $\mathsf{BHist}$ ledger $W$. That entry names the corresponding $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\RealUp$ seal route, $\hsame$ and $\Cont$ transport data, $\Pkg$ provenance, and local $\NameCert$ provenance; no additional window source is available.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_root\_window\_ledger\_exactness}
\begin{proof}
Read the downstream window through \autoref{thm:regular-cauchy-diagonal-window-ledger-exactness}. The theorem identifies the requested window with one of the finite entries in $W$ and records the stream, regular rational, seal-facing, and provenance rows used by that entry.

The root source determinacy theorem above fixes the ambient tuple $D=(Q,S,R,L,W,P,N)$ in which this ledger lives. Hence the selected window cannot be re-read through another $\mathsf{BHist}$ source or through another package row.

Finally, \autoref{thm:regular-cauchy-diagonal-bridge-non-escape} excludes quotient streams, selected host limits, host equality, and ambient completeness rows. The ledger entry is therefore exact for the Real and Completion handoff.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal root seal route exhaustion]
\label{thm:regular-cauchy-diagonal-root-seal-route-exhaustion}
Every $\RealUp$ seal read exported from a root tuple $D=(Q,S,R,L,W,P,N)$ factors through the displayed $\mathsf{BHist}$ route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$, the exact finite ledger $W$, the visible $\hsame$ and $\Cont$ routes, the package row $\Pkg$, and the local $\NameCert$ row. The root packet exports no quotient stream, selected limit, host real equality, or ambient completeness row for the seal.
\end{theorem}
\begin{proof}
Start from the real-seal handoff \autoref{thm:regular-cauchy-diagonal-real-seal-handoff}. It sends the seal request through the stationary rational row, the stream window, the regular rational readback, and the displayed $\RealUp$ seal row.

Use root window-ledger exactness to locate the requested observation inside $W$. This names the precise $\mathsf{BHist}$ entry and attaches the $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already carried by $D$.

The bridge non-escape theorem \autoref{thm:regular-cauchy-diagonal-bridge-non-escape} and mature consumer exhaustion \autoref{thm:regular-cauchy-diagonal-mature-consumer-exhaustion} rule out every remaining completion-side escape coordinate. Thus the seal route is exhausted by the displayed root packet.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_root\_seal\_route\_exhaustion}

\begin{theorem}[Regular Cauchy diagonal root downstream-unblock package]
\label{thm:regular-cauchy-diagonal-root-downstream-unblock-package}
The root obligation surface for $\RegularCauchyDiagonalUp$ is the composition of source determinacy, selector totality, window-ledger exactness, seal route exhaustion, bridge non-escape, and mature consumer exhaustion for the concrete tuple $D=(Q,S,R,L,W,P,N)$. Consequently the $\RealCauchyCompletionUp$ and $\RealDiagonalCompletionUp$ handoff reads only the displayed $\mathsf{BHist}$ route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$, the visible $\hsame$ and $\Cont$ transports, the $\Pkg$ row, and the local $\NameCert$ row.
\end{theorem}
\begin{proof}
First assemble the root source, selector, and window rows. The preceding three theorems fix the tuple $D$, give a displayed selector response for each downstream request, and identify every requested window with an entry of $W$.

Next attach the seal boundary. Root seal route exhaustion identifies the completion-facing object as the same $\RealUp$ seal reached along the route $\RatUp \to \StreamNameUp \to \RegSeqRatUp \to \RealUp$.

Finally compose \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}, \autoref{thm:regular-cauchy-diagonal-mature-consumer-exhaustion}, and \autoref{thm:regular-cauchy-diagonal-downstream-unblock-package}. These rows show that the Real and Completion consumers obtain exactly the displayed packet and no external completion object.
\end{proof}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_root\_downstream\_unblock\_package}

\begin{theorem}[Regular Cauchy diagonal selector-fiber exhaustion]
\label{thm:regular-cauchy-diagonal-selector-fiber-exhaustion}
Every classifier-facing read of an accepted $\RegularCauchyDiagonalUp$ diagonal packet factors through the displayed selector row of its source tuple $D=(Q,S,R,L,W,P,N)$. The factorization reads only the selected finite $\StreamNameUp$ windows in $W$, the corresponding $\DyadicRatCoreUp$ observations, the $\RegSeqRatUp$ row $R$, the $\RealUp$ seal row $L$, and the visible $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance attached to $D$.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_selector\_fiber\_exhaustion}
\begin{proof}
Project the accepted packet to the carrier of \autoref{def:regular-cauchy-diagonal-source}. The carrier exposes exactly the rational seed row, the stream-window row, the regular readback row, the seal row, the finite window ledger, the package row, and the local naming certificate.

Apply \autoref{thm:regular-cauchy-diagonal-window-coverage} and \autoref{thm:regular-cauchy-diagonal-window-ledger-exactness}. These clauses identify every classifier-facing window read with one of the selected entries of $W$ and attach the matching $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ observations.

Finally apply \autoref{thm:regular-cauchy-diagonal-selector-stability} and \autoref{thm:regular-cauchy-diagonal-namecert-consumer-surface}. The remaining reads are precisely the visible transport, package, and naming rows, while the seal-facing coordinate is the displayed $\RealUp$ row supplied by the same source tuple.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal completion-seal composition]
\label{thm:regular-cauchy-diagonal-completion-seal-composition}
The $\RealCauchyCompletionUp$ consumer handoff for an accepted $\RegularCauchyDiagonalUp$ packet is the composition of stationary seal exactness, the bridge obligation package, and the real-completion handoff package. This composition adds no host sequence equality, quotient stream, selected host limit, or ambient completeness data beyond the finite diagonal selector route and the displayed $\RealUp$ seal.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_completion\_seal\_composition}
\begin{proof}
Start with the stationary seal clause of \autoref{thm:regular-cauchy-diagonal-stationary-compatibility}. It fixes the constant rational source route and the associated $\RegSeqRatUp$ readback used by the diagonal selector.

Attach the bridge obligations with \autoref{thm:regular-cauchy-diagonal-standard-bridge-source}, \autoref{thm:regular-cauchy-diagonal-bridge-readback-exactness}, and \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}. These results expose the bridge source, preserve the visible readback, and rule out completion data not carried by the displayed packet.

Now apply \autoref{thm:regular-cauchy-diagonal-selector-fiber-exhaustion} and \autoref{thm:regular-cauchy-diagonal-real-completion-handoff-package}. The selector exhaustion supplies the finite packet route, and the handoff package identifies the completion-facing object as the same $\RealUp$ seal row.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal downstream route factorization]
\label{thm:regular-cauchy-diagonal-downstream-route-factorization}
Every downstream consumer route from an accepted $\RegularCauchyDiagonalUp$ packet through $\DyadicTailBoundUp$, $\RegSeqRatUp$, $\RealUp$, or $\RealCauchyCompletionUp$ factors through the finite diagonal selector route of \autoref{thm:regular-cauchy-diagonal-selector-fiber-exhaustion} and the completion-seal route of \autoref{thm:regular-cauchy-diagonal-completion-seal-composition}. No downstream route obtains an additional carrier, classifier, host equality, quotient, or completion witness outside those two displayed routes.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_downstream\_route\_factorization}
\begin{proof}
First use \autoref{thm:regular-cauchy-diagonal-mature-consumer-exhaustion}. It says that mature consumers of the diagonal packet read the same displayed tuple, finite ledger, readback row, seal row, and local provenance.

Next use \autoref{thm:regular-cauchy-diagonal-downstream-unblock-package}. The downstream package is already the composition of source stability, window-ledger exactness, the public $\NameCert$ surface, and the real-completion handoff package.

The $\DyadicTailBoundUp$, $\RegSeqRatUp$, and $\RealUp$ portions are therefore the selector-fiber route of \autoref{thm:regular-cauchy-diagonal-selector-fiber-exhaustion}. The $\RealCauchyCompletionUp$ portion is the completion-seal composition of \autoref{thm:regular-cauchy-diagonal-completion-seal-composition}, so every listed downstream route factors through those two routes and no extra object is exposed.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal formal target boundary]
\label{thm:regular-cauchy-diagonal-formal-target-boundary}
The formal target for $\RegularCauchyDiagonalUp$ is the finite tuple $D=(Q,S,R,L,W,P,N)$ together with selector-fiber exhaustion, completion-seal composition, downstream route factorization, and bridge non-escape. A Lean target for this chapter should prove only this finite $\BHist$ route over $\RatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and should not prove quotient streams, selected host limits, host equality, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_formal\_target\_boundary}
\begin{proof}
Start with selector-fiber exhaustion from \autoref{thm:regular-cauchy-diagonal-selector-fiber-exhaustion}. It identifies every classifier-facing read with the displayed tuple $D=(Q,S,R,L,W,P,N)$ and the finite window, dyadic, readback, seal, transport, package, and naming rows attached to it.

Next attach completion-seal composition from \autoref{thm:regular-cauchy-diagonal-completion-seal-composition}. The completion-facing consumer reaches the same $\RealUp$ seal by the displayed diagonal selector route rather than by a host sequence equality or selected limit.

Now use downstream route factorization from \autoref{thm:regular-cauchy-diagonal-downstream-route-factorization}. It says that $\DyadicTailBoundUp$, $\RegSeqRatUp$, $\RealUp$, and $\RealCauchyCompletionUp$ consumers all factor through the selector-fiber and completion-seal routes.

Finally apply bridge non-escape from \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}. Since the bridge exports no quotient stream, selected host limit, host equality, or ambient completeness theorem, the finite tuple and its displayed $\BHist$ route are the precise formal target boundary.
\end{proof}

\begin{theorem}[Regular Cauchy diagonal name-normalization handoff]
\label{thm:regular-cauchy-diagonal-name-normalization-handoff}
For every accepted $\RegularCauchyDiagonalUp$ packet whose displayed selector route is read by a $\RegularCauchyNameUp$ normalized readback packet, the $\RealCauchyCompletionUp$ consumer handoff factors through exactly three finite surfaces: the diagonal selector-fiber route, the $\RegularCauchyNameUp$ normalized window readback, and the $\RealCauchyCompletionUp$ downstream consumer handoff. The correspondence excludes quotient streams, host sequence equality, selected host limits, independent real carriers, and ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.RegularCauchyDiagonalUp.RegularCauchyDiagonalCarrier\_name\_normalization\_handoff}
\begin{proof}
Use the formal target boundary of \autoref{thm:regular-cauchy-diagonal-formal-target-boundary}. It restricts the diagonal packet to the finite tuple $D=(Q,S,R,L,W,P,N)$ and the displayed $\BHist$ route over $\RatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

The diagonal contribution is the selector route of \autoref{thm:regular-cauchy-diagonal-downstream-route-factorization}. It says that every downstream $\RegSeqRatUp$, $\RealUp$, or $\RealCauchyCompletionUp$ read from the accepted diagonal packet factors through the selector-fiber route and completion-seal route already present in the same finite packet.

The name contribution is the normalized readback package of \autoref{thm:regularcauchyname-root-unblock-normalization-package}. That package reads the $\RegularCauchyNameUp$ window through its displayed normalized rational-name surface, so the diagonal selector cannot acquire a second host stream, a quotient stream, or an independently selected limit while passing through the name packet.

Finally attach the completion consumer by \autoref{thm:real-cauchy-completion-downstream-consumer-handoff}. Its handoff consumes the regular-family input through the displayed completion packet and does not add an independent real carrier or ambient completeness field. Ledger exhaustion and bridge non-escape leave only the three named surfaces, so the composed route is exactly the diagonal selector-fiber surface, the normalized window readback surface, and the downstream completion handoff surface.
\end{proof}

\closureat{RegularCauchyDiagonalUp}{seedStr}
\closureat{RegularCauchyDiagonalUp}{obligationStr}
\closureat{RegularCauchyDiagonalUp}{scopedStr}
\closureat{RegularCauchyDiagonalUp}{publicStr}
\closureat{RegularCauchyDiagonalUp}{bridgedStr}
\closureat{RegularCauchyDiagonalUp}{matureStr}

\begin{closurestatus}{\RegularCauchyDiagonalUp}
  \constructivestory{A $\RegularCauchyDiagonalUp$ packet is generated from a stationary $\RatUp$ seed row, a $\StreamNameUp$ window row, a $\RegSeqRatUp$ diagonal readback, a $\RealUp$ seal row, finite diagonal-window $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The mature paper scope is the standard bridge source, readback exactness, non-escape boundary, stationary-family exhaustion, and route determinacy of \autoref{thm:regular-cauchy-diagonal-standard-bridge-source}, \autoref{thm:regular-cauchy-diagonal-bridge-readback-exactness}, \autoref{thm:regular-cauchy-diagonal-bridge-non-escape}, \autoref{thm:regular-cauchy-diagonal-stationary-family-exhaustion}, and \autoref{thm:regular-cauchy-diagonal-bridge-route-determinacy}.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient streams, selected host limits, ambient completeness, or bridge checking.}
  \upgradepath{Lean formalization and bridge checking remain for the same diagonal selector and completion-seal interface.}
\end{closurestatus}
