\chapter{A Concrete Naming Certificate for $\AuditTranscriptEnvelopeUp$}
\label{ch:concrete-instances-audit-transcript-envelope-namecert}
\origin{ai}

The $\AuditTranscriptEnvelopeUp$ packet realizes the writing-item discipline of \autoref{def:philosophy-writing-item} as a finite transcript object. It sits between the machine consumer of \autoref{ch:concrete-instances-machine-readable-audit-interface-namecert}, the registry coherence check of \autoref{ch:concrete-instances-registry-consistency-audit-namecert}, and the proof-readback witness of \autoref{ch:concrete-instances-prooftraceauditwitness-namecert}. Those siblings read reports, compare registry rows, and expose proof traces; this carrier names the per-claim envelope that keeps status, source, replay, gap, ledger, and refusal data together before any audit export is consumed.

\begin{definition}[Audit transcript envelope carrier]
\label{def:audit-transcript-envelope-carrier}
An $\AuditTranscriptEnvelopeUp$ carrier is a finite $\BHist$ packet
$$
E=(K,C,L,S,G,A,R,U,H,T,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the claim-kind row, recording whether the writing item is read as a definition, theorem, corollary, proof, schema, report, roadmap, or refusal;
\item $C$ is the carrier/classifier row, recording the BEDC carrier and the classifier or equality surface under which the item is read;
\item $L$ is the ledger row, recording package provenance, dependency entries, and hidden-material refusals visible to the item;
\item $S$ is the theory/formal-status pair, recording the theory-closure grade and formal-verification grade as two separate axes;
\item $G$ is the gap-report row, recording open gaps, refused gaps, closed gaps, and the reason each gap is or is not consumable;
\item $A$ is the source-anchor row, recording the manuscript label, file site, or registry entry from which the writing item is read;
\item $R$ is the replay-checksum row, recording the displayed replay route by which the envelope is reconstructed;
\item $U$ is the not-claimed surface, recording the strongest nearby readings that the envelope explicitly refuses;
\item $H$ records componentwise $\hsame$ transport for claim kind, carrier/classifier, ledger, status-pair, gap, anchor, replay, and not-claimed rows;
\item $T$ records displayed $\Cont$ replay from the source anchor through the checksum row to the machine-readable export boundary;
\item $P$ is the $\Pkg$ provenance over $\AuditTranscriptEnvelopeUp$, $\MachineReadableAuditInterfaceUp$, $\RegistryConsistencyAuditUp$, $\ProofTraceAuditWitnessUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\AuditTranscriptEnvelopeUp}$ row.
\end{enumerate}
The carrier has no coordinate for a hidden proof object, unanchored prose claim, single-axis status collapse, off-ledger gap repair, unchecked replay substitute, or erased not-claimed surface.
\end{definition}
\leandef{BEDC.Derived.AuditTranscriptEnvelopeUp.AuditTranscriptEnvelopeUp}

\begin{theorem}[Audit transcript envelope field coverage]
\label{thm:audit-transcript-envelope-field-coverage}
For the carrier of \autoref{def:audit-transcript-envelope-carrier}, the local $\NameCert_{\AuditTranscriptEnvelopeUp}$ surface consists exactly of five obligation groups:
\begin{enumerate}
\item carrier admission for $E=(K,C,L,S,G,A,R,U,H,T,P,N)$;
\item writing-item exposure through the claim-kind row $K$ and carrier/classifier row $C$;
\item audit-status exactness through the ledger row $L$, theory/formal-status pair $S$, and gap-report row $G$;
\item source and replay accountability through the source-anchor row $A$, replay-checksum row $R$, not-claimed row $U$, transport row $H$, and replay row $T$;
\item package provenance and local naming through $P$ and $N$.
\end{enumerate}
Thus every auditable writing item consumed through this packet is read as one finite transcript envelope, not as a prose sentence with detachable audit metadata.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:audit-transcript-envelope-carrier}. The rows $K,C,L,S,G,A,R,U,H,T,P,N$ are the only coordinates available to the local certificate.

First read the writing-item rows. The kind row $K$ fixes the permitted claim type, and $C$ fixes the carrier/classifier surface on which that claim is meaningful.

Next read the audit rows. The ledger row $L$, status pair $S$, and gap row $G$ state what the claim depends on, which paper-side and verification-side grades it carries, and which gaps are exposed or refused.

Finally inspect $A,R,U,H,T,P,N$. These rows anchor the claim, replay the envelope, preserve the not-claimed surface, transport the displayed coordinates, record provenance, and name the packet. Since no further coordinate remains, the five obligation groups exhaust the local $\NameCert_{\AuditTranscriptEnvelopeUp}$ surface.
\end{proof}

\begin{theorem}[Audit transcript envelope non-evidence refusal]
\label{thm:audit-transcript-envelope-non-evidence-refusal}
If an $\AuditTranscriptEnvelopeUp$ carrier lacks either the theory/formal-status pair $S$ or the replay-checksum row $R$, then no accepted $\MachineReadableAuditInterfaceUp$ export may consume the envelope as theorem evidence.
\end{theorem}
\begin{proof}
Begin with an accepted envelope
$$
E=(K,C,L,S,G,A,R,U,H,T,P,N).
$$
The machine-readable consumer of \autoref{ch:concrete-instances-machine-readable-audit-interface-namecert} reads audit data through displayed schema, checker, export, refusal, report, transport, replay, provenance, and local naming rows.

If $S$ is absent, the consumer cannot distinguish paper-side closure from Lean-side verification status. If $R$ is absent, the consumer has no checksum row tying the displayed transcript to a replay route.

In either case the requested theorem-evidence reading is stronger than the envelope supplies. The only available response is the non-evidence refusal recorded by the audit interface, so the envelope may still be reported but not consumed as theorem evidence.
\end{proof}

\begin{theorem}[Audit transcript envelope sibling independence]
\label{thm:audit-transcript-envelope-sibling-independence}
The $\AuditTranscriptEnvelopeUp$ carrier is not bijective, under NameCert-row preservation, to $\MachineReadableAuditInterfaceUp$, $\ProofTraceAuditWitnessUp$, $\RegistryConsistencyAuditUp$, or $\MachineInterfaceFormalizationTargetUp$.
\end{theorem}
\begin{proof}
Compare row inventories. $\MachineReadableAuditInterfaceUp$ supplies schema, checker, export, refusal, and report rows for a machine consumer, but it does not store the per-claim source anchor, replay checksum, and not-claimed surface as one writing-item envelope.

$\ProofTraceAuditWitnessUp$ binds a proof trace to source, classifier, transport, forbidden-resource refusal, verdict, provenance, and local naming. It does not carry the theory/formal-status pair or the gap report required for a general writing item.

$\RegistryConsistencyAuditUp$ compares registry entries and status agreement across exports, while $\MachineInterfaceFormalizationTargetUp$ stores formal target skeletons and machine-facing target data. Neither is a per-claim transcript envelope with all of $K,C,L,S,G,A,R,U$ displayed together.

Any NameCert-row-preserving bijection would have to preserve each of claim kind, carrier/classifier row, ledger row, status pair, gap report, source anchor, replay checksum, and not-claimed surface. Each named sibling omits at least one of those rows, so no such bijection exists.
\end{proof}

\begin{theorem}[Audit transcript envelope falsifiable prediction]
\label{thm:audit-transcript-envelope-falsifiable-prediction}
An $\AuditTranscriptEnvelopeUp$ carrier is rejected as a machine-consumable audit transcript exactly when a consumer asks for a theorem-evidence, registry-consistency, or proof-readback consequence not backed by its displayed kind, carrier/classifier, ledger, status-pair, gap, source-anchor, replay-checksum, not-claimed, transport, replay, provenance, and local naming rows.
\end{theorem}
\begin{proof}
Use \autoref{thm:audit-transcript-envelope-field-coverage} to read the complete envelope inventory. Every accepted read factors through $K,C,L,S,G,A,R,U,H,T,P,N$.

For theorem-evidence reads, inspect the status pair $S$ and replay checksum $R$ together with \autoref{thm:audit-transcript-envelope-non-evidence-refusal}. For registry-consistency reads, inspect $L,S,G,A$ and the provenance row $P$ naming the registry audit surface. For proof-readback reads, inspect $C,L,A$ and the provenance row naming the proof-trace witness.

If one of those rows is absent, disagrees with the requested consequence, or is refused by $U$, the consumer has left the envelope. Conversely a consequence backed by the displayed rows is precisely the finite audit transcript reading exposed by this carrier.
\end{proof}

\falsifiablePrediction{If an envelope omits either the closure-status row or the replay checksum row, then it cannot be consumed by a MachineReadableAuditInterfaceUp export without a non-evidence refusal.}

\independenceWitness{machinereadableauditinterface, prooftraceauditwitness, registryconsistencyaudit, machineinterfaceformalizationtarget: none is bijective to AuditTranscriptEnvelopeUp because each omits at least one of per-claim status-pair, source-anchor, replay-checksum, or not-claimed rows.}

The Lean follow-up must provide explicit $\Nontrivial\ \AuditTranscriptEnvelopeUp$ and $\FieldFaithful\ \AuditTranscriptEnvelopeUp$ instances in \texttt{lean4/BEDC/Derived/AuditTranscriptEnvelopeUp/TasteGate.lean}. The field-faithfulness witness must preserve $K,C,L,S,G,A,R,U,H,T,P,N$ as separate displayed fields before $\mathsf{BEDC.Derived.AuditTranscriptEnvelopeUp.taste\_gate}$ can be cited by a checked paper marker.

\closureat{AuditTranscriptEnvelopeUp}{seedStr}
\closureat{AuditTranscriptEnvelopeUp}{obligationStr}

\begin{closurestatus}{\AuditTranscriptEnvelopeUp}
  \constructivestory{An $\AuditTranscriptEnvelopeUp$ packet is generated from claim kind, carrier/classifier, ledger, theory/formal-status, gap, source-anchor, replay-checksum, not-claimed, transport, replay, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:audit-transcript-envelope-carrier}, \autoref{thm:audit-transcript-envelope-field-coverage}, \autoref{thm:audit-transcript-envelope-non-evidence-refusal}, \autoref{thm:audit-transcript-envelope-sibling-independence}, and \autoref{thm:audit-transcript-envelope-falsifiable-prediction} bind auditable writing items to finite transcript envelopes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, bridge checking, registry completeness, proof-trace correctness, machine export schema completeness, or global audit log finality.}
  \upgradepath{Obligation closure requires checked carrier admission, five-row NameCert coverage, non-evidence refusal, sibling independence, TasteGate nontriviality, and field faithfulness for $K,C,L,S,G,A,R,U,H,T,P,N$.}
\end{closurestatus}
