\chapter{A Concrete Naming Certificate for $\DiagonalRegularitySealUp$}
\label{ch:concrete-instances-diagonalregularityseal-namecert}
\origin{ai}

The $\DiagonalRegularitySealUp$ packet realizes the diagonal-regularity theorem of \autoref{sec:real-completeness-regular-cauchy} as a finite theorem-facing seal before the terminal Real handoff. It binds the representative route of \autoref{ch:concrete-instances-diagonallimitrepresentative-namecert}, the endpoint and middle estimates organized by \autoref{ch:concrete-instances-dyadic-tolerance-triangle-ledger-namecert}, and the regularity witness of \autoref{ch:concrete-instances-regular-cauchy-regularity-witness-namecert} into one NameCert surface. The packet is consumed by Real-completion routes such as \autoref{ch:concrete-instances-real-diagonal-regularity-seal-namecert}, but it does not itself assert quotient stream equality, selected host limits, host real equality, countable choice, or ambient completeness.

\begin{definition}[Diagonal regularity-seal carrier]
\label{def:diagonal-regularity-seal-carrier}
A $\DiagonalRegularitySealUp$ carrier is a finite $\BHist$ packet
$$
S=(D,E_0,E_1,M,Q,W,R,Z,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $D$ is the accepted $\DiagonalLimitRepresentativeUp$ row selecting the diagonal representative and its modulus readbacks.
\item $E_0$ and $E_1$ are the two endpoint-leg rows that read the regular-rational endpoints used in the triangle estimate.
\item $M$ is the middle-modulus leg row exposing the regular Cauchy comparison between the selected representatives.
\item $Q$ is the $\DyadicToleranceTriangleLedgerUp$ row that records the endpoint tolerances, middle tolerance, dyadic sum, and output tolerance bound.
\item $W$ is the finite window-factorization row listing the endpoint windows, the shared intermediate window, and the requested output window.
\item $R$ is the $\RegularCauchyRegularityWitnessUp$ row that packages the diagonal-regularity witness for downstream consumers.
\item $Z$ is the optional downstream Real-seal row, used only as a terminal named handoff and never as hidden completeness evidence.
\item $H$ records componentwise $\hsame$ transport for $D,E_0,E_1,M,Q,W,R,Z$ and the local certificate row.
\item $C$ records displayed $\Cont$ replay from the representative row through the endpoint legs, middle modulus leg, dyadic tolerance row, window factorization, regularity witness, and terminal seal.
\item $P$ is the $\Pkg$ provenance over $\DiagonalRegularitySealUp$, $\DiagonalLimitRepresentativeUp$, $\DyadicToleranceTriangleLedgerUp$, $\RegularCauchyRegularityWitnessUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\DiagonalRegularitySealUp}$ row.
\end{enumerate}
The carrier has no coordinate for quotient stream equality, selected host limits, host real equality, countable choice, detached completion evidence, or an ambient completeness theorem.
\end{definition}

\begin{definition}[Diagonal regularity-seal classifier]
\label{def:diagonal-regularity-seal-classifier}
Two accepted $\DiagonalRegularitySealUp$ carriers classify together only when their representative rows, endpoint legs, middle-modulus legs, dyadic tolerance rows, finite windows, regularity-witness rows, terminal seal rows, transport rows, continuation rows, package rows, and local naming rows are related componentwise by displayed $\hsame$ data and replayed along the same $\Cont$ route. The classifier does not identify packets by host equality of real numbers, by quotienting streams, by deleting either endpoint leg, by hiding the middle modulus leg, or by replacing the dyadic tolerance row with an ambient completeness appeal.
\end{definition}

\begin{theorem}[Diagonal regularity-seal obligations]
\label{thm:diagonal-regularity-seal-obligations}
For every accepted $\DiagonalRegularitySealUp$ carrier $S=(D,E_0,E_1,M,Q,W,R,Z,H,C,P,N)$, the local $\NameCert_{\DiagonalRegularitySealUp}$ surface consists exactly of carrier exposure, classifier transport, representative exposure through $D$, endpoint-leg exposure through $E_0$ and $E_1$, middle-modulus exposure through $M$, dyadic tolerance-sum exposure through $Q$, finite window factorization through $W$, regularity-witness exposure through $R$, terminal Real-seal handoff through $Z$, componentwise transport through $H$, displayed continuation replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.DiagonalRegularitySealUp.DiagonalRegularitySealTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier exposure is projection from \autoref{def:diagonal-regularity-seal-carrier}. The tuple displays the representative row, the two endpoint legs, the middle modulus leg, the dyadic tolerance row, the finite windows, the regularity witness, the terminal seal, and the structural support rows.

Classifier transport is exactly the relation of \autoref{def:diagonal-regularity-seal-classifier}. It keeps each displayed row on the same componentwise transported route.

The data-bearing obligations are read from the cited sibling chapters. The representative row comes from \autoref{ch:concrete-instances-diagonallimitrepresentative-namecert}; the dyadic tolerance surface supplies the endpoint and middle tolerance arithmetic through \autoref{ch:concrete-instances-dyadic-tolerance-triangle-ledger-namecert}; and the regularity witness comes from \autoref{ch:concrete-instances-regular-cauchy-regularity-witness-namecert}.

Since $H,C,P,N$ only transport, replay, source, and name those displayed rows, the listed clauses exhaust the local seal surface.
\end{proof}

\begin{theorem}[Diagonal regularity-seal nonescape]
\label{thm:diagonal-regularity-seal-nonescape}
An accepted $\DiagonalRegularitySealUp$ carrier exports only the displayed rows $D,E_0,E_1,M,Q,W,R,Z,H,C,P,N$ and their classifier transports. No consumer can replace the representative row, either endpoint leg, the middle modulus leg, the dyadic tolerance row, the finite window factorization, or the regularity witness by quotient stream equality, selected host limits, host real equality, countable choice, detached completion evidence, or an ambient completeness theorem.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:diagonal-regularity-seal-carrier}. Every exported coordinate is a displayed BEDC row or structural support for transport, continuation replay, provenance, and naming.

\autoref{thm:diagonal-regularity-seal-obligations} accounts for the admissible carrier and classifier rows. No additional equality, selection, choice, or completeness coordinate appears in that list.

The excluded objects require coordinates absent from the carrier. Therefore neither the local $\NameCert$ row nor any displayed continuation can export them in place of the finite diagonal-regularity seal.
\end{proof}

\begin{theorem}[Diagonal regularity-seal window factorization]
\label{thm:diagonal-regularity-seal-window-factorization}
Every consumer of an accepted $\DiagonalRegularitySealUp$ packet factors its diagonal-regularity request through the finite route
$$
D,E_0,E_1,M,Q,W,R,Z,H,C,P,N.
$$
The window row $W$ separates the two endpoint observations, the shared middle comparison window, the dyadic tolerance output, and the terminal Real-seal handoff, so the consumer reaches the theorem seal only after reading the representative row, both endpoint legs, the middle modulus leg, and the dyadic tolerance row.
\end{theorem}
\begin{proof}
Begin with the representative route. The row $D$ fixes the diagonal representative and the modulus-index readbacks before any endpoint or middle comparison can be consumed.

Next read the three estimate legs. The endpoint rows $E_0,E_1$ expose the regular-rational endpoint bounds, while $M$ exposes the middle Cauchy-modulus comparison. The dyadic row $Q$ records the tolerance arithmetic that combines these three legs into the output bound.

Finally factor the route through $W,R,Z,H,C,P,N$. The window row records the finite observations needed by the theorem, the witness row packages the regularity evidence, and the terminal Real-seal row remains downstream of the same displayed route. Hence every consumer factors through the ordered finite packet shown above.
\end{proof}

\falsifiablePrediction{A diagonal regularity consumer that reaches the Real seal while omitting the representative row, either endpoint leg, the middle modulus leg, or the dyadic tolerance row refutes the packet.}

\independenceWitness{diagonallimitrepresentative, dyadic-tolerance-triangle-ledger, regular-cauchy-regularity-witness, streamname, real: no listed sibling is bijective to $\DiagonalRegularitySealUp$ because this packet binds the representative, three-leg estimate, dyadic tolerance output, finite windows, and terminal Real seal as one consumer-facing seal.}

Lean follow-up must add explicit $\mathsf{Nontrivial}\ \DiagonalRegularitySealUp$ and $\mathsf{FieldFaithful}\ \DiagonalRegularitySealUp$ instances in \texttt{lean4/BEDC/Derived/DiagonalRegularitySealUp/TasteGate.lean}.

\closureat{DiagonalRegularitySealUp}{seedStr}

\begin{closurestatus}{\DiagonalRegularitySealUp}
  \constructivestory{A $\DiagonalRegularitySealUp$ packet is generated from a diagonal representative row, two endpoint-leg rows, a middle-modulus row, a dyadic tolerance ledger, a finite window factorization, a regularity witness, a terminal Real-seal handoff, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:diagonal-regularity-seal-carrier}, \autoref{def:diagonal-regularity-seal-classifier}, \autoref{thm:diagonal-regularity-seal-obligations}, \autoref{thm:diagonal-regularity-seal-nonescape}, and \autoref{thm:diagonal-regularity-seal-window-factorization} bind the finite diagonal-regularity theorem seal surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, quotient stream equality, selected host limits, host real equality, countable choice, detached completion evidence, or ambient completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, nonescape, window factorization, and TasteGate nontriviality with field faithfulness for $D,E_0,E_1,M,Q,W,R,Z,H,C,P,N$.}
\end{closurestatus}
