\chapter{A Concrete Naming Certificate for $\FocusedLedgerUp$}
\label{ch:concrete-instances-focused-ledger-namecert}
\origin{ai}

The $\FocusedLedgerUp$ packet realizes the finite focused multi-Hist ledger of \autoref{subsec:philosophy-focused-multi-hist-ledgers} and \autoref{def:philosophy-focused-multi-hist-ledger} as a concrete NameCert carrier. It sits beside $\ConsciousUniverseSpaceUp$ in \autoref{ch:concrete-instances-consciousuniversespace-namecert}, $\ObserverHistIdentityUp$ in \autoref{ch:concrete-instances-observerhistidentity-namecert}, $\InterHistLocalityLedgerUp$ in \autoref{ch:concrete-instances-inter-hist-locality-ledger-namecert}, $\InscriptionEventUp$ in \autoref{ch:concrete-instances-inscriptionevent-namecert}, and $\OnticResidueLedgerUp$ in \autoref{ch:concrete-instances-ontic-residue-ledger-namecert}. Those siblings consume histories, identity rows, locality rows, inscription events, or residue rows; this packet binds the whole focus-selector-digest-gap-relation-invariant-audit tuple before those readings are separated.

\begin{definition}[Focused ledger carrier]
\label{def:focused-ledger-carrier}
A $\FocusedLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(I,H,T,F,S,D,G,R,J,Q,\rho,A,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $I$ is the finite index ledger naming the available history slots;
\item $H$ assigns a finite $\Hist$ row to each slot of $I$;
\item $T$ records local continuation chains for the displayed histories, without adding a global scalar clock;
\item $F$ is the focus index selecting the visible history slot;
\item $S$ is the selector ledger that records the branch choices and focus reads used by $F$;
\item $D$ is the digest ledger recording finite summaries whose provenance remains displayed;
\item $G$ is the gap and provenance row recording boundary pressure, missing observations, and source data for each digest;
\item $R$ is the inter-history relation row;
\item $J$ is the inter-history invariant row;
\item $Q$ is the dependence row, including optional maximum-rate readings when such rows are present;
\item $\rho$ is the focused self-proxy row for the selected history;
\item $A$ is the audit row refusing subject parameters, global clocks, hidden choosers, unledgered compression, object-level $T$, and hidden dependence on meta-closure;
\item $C$ records displayed $\Cont$ replay across $I,H,T,F,S,D,G,R,J,Q,\rho,A$;
\item $P$ records $\Pkg$ provenance over $\FocusedLedgerUp$, $\FocusedMultiHistLedgerUp$, $\ConsciousUniverseSpaceUp$, $\ObserverHistIdentityUp$, $\InterHistLocalityLedgerUp$, $\InscriptionEventUp$, $\OnticResidueLedgerUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\FocusedLedgerUp}$ row.
\end{enumerate}
The carrier has no coordinate for a subject substance, ambient universe object, hidden scheduler, unrecorded quotient of histories, object-level time object, or meta-closure oracle.
\end{definition}

\begin{theorem}[Focused ledger audit closure]
\label{thm:focused-ledger-audit-closure}
For the carrier of \autoref{def:focused-ledger-carrier}, the audit row $A$ closes exactly the refusals of no subject, no global clock, no hidden chooser, no unledgered compression, no object-level $T$, and no hidden meta-closure dependence. Every accepted $\FocusedLedgerUp$ consumer must read focus, selection, digest, gap, relation, invariant, dependence, self-proxy, replay, provenance, and local naming through
$$
I,H,T,F,S,D,G,R,J,Q,\rho,A,C,P,N.
$$
\end{theorem}
\begin{proof}
Project the carrier. The rows $I,H,T,F,S,D,G,R,J,Q,\rho$ expose the finite histories, focus, selector, digest, gap, relation, invariant, dependence, and self-proxy data that the packet is allowed to use.

Read the audit row next. The no-subject refusal prevents a hidden owner coordinate; the no-global-clock refusal keeps $T$ local; the no-hidden-chooser refusal forces all branch choice through $S$; the no-unledgered-compression refusal keeps summaries tied to $D$ and $G$; the no object-level $T$ refusal prevents a time object from replacing the local continuation rows; and the no hidden meta-closure refusal prevents the packet from citing a closure source not displayed in $A$.

Finally use the structural rows. The replay row $C$, provenance row $P$, and local name $N$ preserve and name only the displayed packet, so no consumer can recover an omitted subject, clock, chooser, compression, time object, or meta-closure dependency from the certificate surface.
\end{proof}

\begin{theorem}[Focused ledger NameCert obligation surface]
\label{thm:focused-ledger-namecert-obligation-surface}
The local $\NameCert_{\FocusedLedgerUp}$ surface for \autoref{def:focused-ledger-carrier} consists of exactly five obligation rows:
\begin{enumerate}
\item carrier admission for the finite packet $L=(I,H,T,F,S,D,G,R,J,Q,\rho,A,C,P,N)$;
\item classifier stability for the selected history, selector ledger, digest ledger, relation row, invariant row, dependence row, and self-proxy row under componentwise $\hsame$ transport;
\item continuation exactness for the displayed $\Cont$ routes in $C$ and no replay route outside the finite index ledger $I$;
\item audit-row exactness for the six refusals recorded in $A$;
\item provenance and local naming through $P$ and $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
The carrier definition displays all content rows before transport, replay, provenance, and naming. The first obligation admits that finite packet as the only carrier surface.

The second and third obligations are forced by the BEDC structural rows: $\hsame$ transport preserves the selected carrier fields componentwise, and $\Cont$ replay is read only through $C$.

The fourth obligation is \autoref{thm:focused-ledger-audit-closure}. The fifth obligation is the terminal NameCert packaging: $P$ records the source rows and $N$ names the accepted packet. No sixth obligation is available, because every accepted consumer already factors through the displayed carrier.
\end{proof}

\begin{theorem}[Focused ledger sibling independence]
\label{thm:focused-ledger-sibling-independence}
$\FocusedLedgerUp$ is not bijective with $\ConsciousUniverseSpaceUp$, $\ObserverHistIdentityUp$, $\InterHistLocalityLedgerUp$, $\InscriptionEventUp$, or $\OnticResidueLedgerUp$. The focused ledger carries the whole focus-selector-digest-gap-relation-invariant-audit tuple, while each sibling omits at least one of the required focused-ledger rows or one audit refusal.
\end{theorem}
\begin{proof}
Compare the carrier inventories. $\ConsciousUniverseSpaceUp$ reads universe-slice, locality-cell, local-time, and trace-identity structure after a focused ledger row is available, but it does not carry the full selector, digest, gap, relation, invariant, dependence, and audit tuple of \autoref{def:focused-ledger-carrier}.

$\ObserverHistIdentityUp$ supplies observer-history identity rows, and $\InterHistLocalityLedgerUp$ supplies inter-history locality rows. Neither packet contains the focused selector ledger, digest provenance, self-proxy, and six-refusal audit row together.

$\InscriptionEventUp$ records inscription-event admission, while $\OnticResidueLedgerUp$ records residue-bearing observation structure. Those packets can consume focused-ledger information, but neither contains the whole finite packet $I,H,T,F,S,D,G,R,J,Q,\rho,A,C,P,N$. Therefore no sibling is bijective with $\FocusedLedgerUp$ as a NameCert carrier.
\end{proof}

\falsifiablePrediction{A $\FocusedLedgerUp$ packet cannot be reduced to an $\InscriptionEventUp$ packet without losing at least the selector, digest, relation, invariant, or audit row.}

\independenceWitness{consciousuniversespace, observerhistidentity, interhistlocalityledger, inscriptionevent, onticresidueledger: none is bijective with $\FocusedLedgerUp$ because each omits at least one required focused-ledger row or audit refusal.}

The Lean TasteGate file \texttt{lean4/BEDC/Derived/FocusedLedgerUp/TasteGate.lean} must provide explicit $\mathsf{Nontrivial}\ \FocusedLedgerUp$ and $\mathsf{FieldFaithful}\ \FocusedLedgerUp$ instances over the same finite carrier.

\closureat{FocusedLedgerUp}{seedStr}

\begin{closurestatus}{\FocusedLedgerUp}
  \constructivestory{A $\FocusedLedgerUp$ packet is generated from finite history slots, local continuation rows, a focus index, selector rows, digest rows, gap and provenance rows, relation rows, invariant rows, dependence rows, a self-proxy row, audit refusals, Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:focused-ledger-carrier}, \autoref{thm:focused-ledger-audit-closure}, \autoref{thm:focused-ledger-namecert-obligation-surface}, and \autoref{thm:focused-ledger-sibling-independence} bind the finite focused multi-Hist ledger as a concrete NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, public-object export, global spacetime, subject substance, or hidden meta-closure.}
  \upgradepath{Lean closure requires Nontrivial FocusedLedgerUp and FieldFaithful FocusedLedgerUp instances in \texttt{lean4/BEDC/Derived/FocusedLedgerUp/TasteGate.lean}.}
\end{closurestatus}
