\chapter{A Concrete Naming Certificate for $\ConceptRegistrySurfaceUp$}
\label{ch:concrete-instances-concept-registry-surface-namecert}
\origin{ai}

The $\ConceptRegistrySurfaceUp$ packet realizes the registry family of \autoref{def:philosophy-registry-family} and the concept-entry discipline of \autoref{def:philosophy-concept-registry-entry} as a finite NameCert carrier. It sits beside the export-control packet of \autoref{ch:concrete-instances-registry-export-surface-namecert}, the failed-gate witness of \autoref{ch:concrete-instances-auditgatefailurewitness-namecert}, and the auditable-generativity package of \autoref{ch:visions-philosophy-auditable-generativity}. Those siblings expose registry export, diagnostic failure, or package-level vision rows; this packet binds concept entry, theorem entry, gap entry, tradition entry, science entry, cannot-claim row, upgrade route, transport, provenance, and local naming before a philosophical concept can leave the registry family as BEDC prose.

\begin{definition}[Concept registry surface carrier]
\label{def:concept-registry-surface-carrier}
A $\ConceptRegistrySurfaceUp$ carrier is a finite $\BHist$ packet
$$
Q=(C,T,G,R,S,F,U,H,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $C$ is the concept-entry row, recording the concept name, BEDC site, carrier, classifier, ledger, positive reading, forbidden readings, gap status, closure status, and formal status.
\item $T$ is the theorem-entry row, recording the theorem or theorem-facing obligation to which the concept may point.
\item $G$ is the gap-entry row, recording the visible socket, missing proof, boundary pressure, or formalization target carried by the concept.
\item $R$ is the tradition-entry row, recording comparison with inherited philosophical vocabulary without turning that comparison into package membership.
\item $S$ is the science-entry row, recording empirical or records-side claims whose export remains tied to displayed observations and prediction sockets.
\item $F$ is the cannot-claim row, recording the forbidden readings that block export as subject substance, global world object, hidden theorem, primitive law, or unlicensed term.
\item $U$ is the upgrade-route row, recording the route by which a concept may move to a stronger registry status after a displayed carrier, theorem, gap, or bridge row is present.
\item $H$ stores componentwise $\hsame$ transport for concept, theorem, gap, tradition, science, cannot-claim, upgrade, provenance, and local naming rows.
\item $P$ is the $\Pkg$ provenance over $\ConceptRegistrySurfaceUp$, $\RegistryExportSurfaceUp$, $\AuditGateFailureWitnessUp$, $\AxisZeckendorfCannotClaimUp$, philosophy-package registry rows, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\ConceptRegistrySurfaceUp}$ row.
\end{enumerate}
The carrier has no coordinate for a concept with no displayed BEDC site, no forbidden-reading row, no registry route, or no local naming row.
\end{definition}
\leandef{BEDC.Derived.ConceptRegistrySurfaceUp.ConceptRegistrySurfaceCarrier}

\begin{theorem}[Concept registry surface export exactness]
\label{thm:concept-registry-surface-export-exactness}
For the carrier of \autoref{def:concept-registry-surface-carrier}, the local $\NameCert_{\ConceptRegistrySurfaceUp}$ surface consists exactly of five obligation rows:
\begin{enumerate}
\item carrier admission for $Q=(C,T,G,R,S,F,U,H,P,N)$;
\item concept-entry exactness through $C$, requiring the displayed BEDC site, carrier, classifier, ledger, positive reading, forbidden readings, gap status, closure status, and formal status to remain in one row;
\item registry-family coverage through $T,G,R,S,F,U$, requiring theorem, gap, tradition, science, cannot-claim, and upgrade readings to be displayed before export;
\item componentwise transport and displayed route replay through $H$ and the registry routes named in $P$;
\item package provenance and local naming through $P$ and $N$.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the finite packet of \autoref{def:concept-registry-surface-carrier}. The concept row $C$ contains the exact entry fields required by the concept registry, while $T,G,R,S,F,U$ place the same concept inside the theorem, gap, tradition, science, cannot-claim, and upgrade routes of the registry family.

The export-control surface of \autoref{ch:concrete-instances-registry-export-surface-namecert} supplies the public reading discipline: a concept leaves the philosophy package only through displayed registration, status, blocking, audit, and non-smuggling rows. Here those rows are specialized to the concept-entry exactness carried by $C$ and to the registry-family rows $T,G,R,S,F,U$.

Finally $H,P,N$ transport, package, and name the same packet. Since $Q$ contains no hidden registry state or prose-only export coordinate, the five rows listed in the statement exhaust the local $\NameCert_{\ConceptRegistrySurfaceUp}$ surface.
\end{proof}
\leanchecked{BEDC.Derived.ConceptRegistrySurfaceUp.ConceptRegistrySurface\_export\_exactness\_certificate}

\begin{theorem}[Concept registry surface forbidden-reading refusal]
\label{thm:concept-registry-surface-forbidden-reading-refusal}
Every accepted $\ConceptRegistrySurfaceUp$ packet refuses export of a philosophical concept that lacks one of the displayed BEDC site in $C$, forbidden-reading row $F$, registry-family route $T,G,R,S,U$, transport row $H$, provenance row $P$, or local naming row $N$. A consumer cannot replace those rows by prose synthesis, inherited tradition, scientific vocabulary, host semantics, or an audit-gate failure read as theorem content.
\end{theorem}
\leanchecked{BEDC.Derived.ConceptRegistrySurfaceUp.ConceptRegistrySurface\_forbidden\_reading\_refusal\_certificate}
\begin{proof}
Use \autoref{thm:concept-registry-surface-export-exactness}. It binds every exportable concept to the displayed concept entry and to the theorem, gap, tradition, science, cannot-claim, and upgrade rows of the same finite packet.

If the BEDC site in $C$ is absent, the concept remains external vocabulary rather than an accepted registry entry. If the forbidden-reading row $F$ is absent, the packet no longer records which readings are blocked, so it cannot be an accepted concept-registry export.

The sibling failure surface of \autoref{ch:concrete-instances-auditgatefailurewitness-namecert} records failed gate items as diagnostic refusal data. It does not convert a missing concept row or missing forbidden-reading row into theorem content. Package provenance and local naming preserve the displayed refusal route; they do not add a hidden export path.
\end{proof}

\falsifiablePrediction{An exported philosophical concept without a displayed BEDC site, forbidden-reading row, and registry route is outside ConceptRegistrySurfaceUp.}

\independenceWitness{registryexportsurface, auditgatefailurewitness, cannotclaimregistry, conceptregistry, philosophypackage: none is bijective because ConceptRegistrySurfaceUp carries the concept-entry exactness and forbidden-reading route simultaneously while each sibling lacks at least one of those rows.}

The Lean follow-up for $\ConceptRegistrySurfaceUp$ must provide $\mathsf{Nontrivial}\ \ConceptRegistrySurfaceUp$ and $\mathsf{FieldFaithful}\ \ConceptRegistrySurfaceUp$ instances in \texttt{lean4/BEDC/Derived/ConceptRegistrySurfaceUp/TasteGate.lean}. The instances must preserve the concept, theorem, gap, tradition, science, cannot-claim, upgrade, transport, provenance, and local NameCert rows of $Q=(C,T,G,R,S,F,U,H,P,N)$ before any later checked theorem cites the carrier as a TasteGate surface.

\closureat{ConceptRegistrySurfaceUp}{seedStr}

\begin{closurestatus}{\ConceptRegistrySurfaceUp}
  \constructivestory{A $\ConceptRegistrySurfaceUp$ packet is generated from concept, theorem, gap, tradition, science, cannot-claim, upgrade, componentwise hsame transport, package provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:concept-registry-surface-carrier}, \autoref{thm:concept-registry-surface-export-exactness}, and \autoref{thm:concept-registry-surface-forbidden-reading-refusal} bind concept-registry export to a finite registry-family packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, complete philosophy-package governance, or correctness of every downstream concept registry entry.}
  \upgradepath{Lean closure requires Nontrivial ConceptRegistrySurfaceUp and FieldFaithful ConceptRegistrySurfaceUp instances in \texttt{lean4/BEDC/Derived/ConceptRegistrySurfaceUp/TasteGate.lean}.}
\end{closurestatus}
