\chapter{A Concrete Naming Certificate for $\LogicContradictionMetaLoopUp$}
\label{ch:concrete-instances-logiccontradictionmetaloop-namecert}
\origin{ai}

The $\LogicContradictionMetaLoopUp$ packet realizes the logic and meta-loop boundary of \autoref{sec:visions-philosophy-logic-contradiction-meta-loop} as a finite NameCert carrier. It sits after the quotient refusal surface of \autoref{ch:concrete-instances-quotient-soundness-boundary-namecert} and the failed audit witness of \autoref{ch:concrete-instances-auditgatefailurewitness-namecert}. Those siblings refuse representative collapse and expose failed gate diagnostics, while the present packet binds proof-pattern discipline, local refutation, open meta-loop refusal, audit-gate failure, transport, route replay, provenance, and local naming before any consumer may read a logical closure claim.

\begin{definition}[Logic contradiction meta-loop carrier]
\label{def:logic-contradiction-meta-loop-carrier}
A $\LogicContradictionMetaLoopUp$ carrier is a finite $\BHist$ packet
$$
L=(P,R,M,A,T,C,G,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the finite proof-pattern row recording constructive formation, introduction, elimination, and local refutation steps;
\item $R$ is the local-refutation row that records a witnessed contradiction only as a bounded failure of the displayed proof pattern;
\item $M$ is the open meta-loop refusal row, rejecting total truth, unrestricted choice, quotient collapse, and halting closure as consumer-readable coordinates;
\item $A$ is the audit-gate row, with failed reads routed through the $\AuditGateFailureWitnessUp$ surface;
\item $T$ records componentwise $\hsame$ transport for proof-pattern, refutation, meta-loop refusal, audit gate, route, provenance, and local naming rows;
\item $C$ records the displayed $\Cont$ replay from proof-pattern inspection through local refutation and open meta-loop refusal into the audit gate;
\item $G$ is the $\Pkg$ provenance over $\LogicContradictionMetaLoopUp$, $\QuotientSoundnessBoundaryUp$, $\AuditGateFailureWitnessUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\LogicContradictionMetaLoopUp}$ row.
\end{enumerate}
The local classifier compares accepted carriers only through the visible rows $P,R,M,A,T,C,G,N$ and has no coordinate for total truth, global choice, quotient equality elimination, or a halting oracle.
\end{definition}

\begin{theorem}[Logic contradiction meta-loop NameCert obligations]
\label{thm:logic-contradiction-meta-loop-namecert-obligations}
For every accepted $\LogicContradictionMetaLoopUp$ carrier
$$
L=(P,R,M,A,T,C,G,N),
$$
the local $\NameCert_{\LogicContradictionMetaLoopUp}$ surface consists exactly of proof-pattern admission through $P$, local-refutation exposure through $R$, open meta-loop refusal through $M$, audit-gate failure routing through $A$, componentwise transport through $T$, displayed continuation replay through $C$, package provenance through $G$, local naming through $N$, and non-admission of total truth, unrestricted choice, quotient collapse, and halting closure.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:logic-contradiction-meta-loop-carrier}. Each admitted proof-pattern, refutation, meta-loop refusal, audit-gate, transport, continuation, provenance, and naming row is a displayed coordinate of the finite packet.

The quotient side is already constrained by \autoref{ch:concrete-instances-quotient-soundness-boundary-namecert}: a quotient-like consumer receives a refusal-and-transport surface rather than a representative selector or a $\mathsf{Quot.sound}$ row. The present carrier records that refusal in $M$ and transports it only through $T,C,G,N$.

The audit side is constrained by \autoref{ch:concrete-instances-auditgatefailurewitness-namecert}: a failed gate read must expose its diagnostic row before it reaches a refusal target. The present carrier records that dependency in $A$ and does not promote the failed item to theorem content.

Thus the local NameCert surface is exhausted by the eight displayed rows. There is no remaining coordinate from which a consumer could read total truth, unrestricted choice, quotient collapse, or halting closure.
\end{proof}

\begin{theorem}[Logic contradiction meta-loop non-escape]
\label{thm:logic-contradiction-meta-loop-nonescape}
An accepted $\LogicContradictionMetaLoopUp$ carrier cannot export a route from local contradiction management to total truth, unrestricted choice, quotient equality elimination, global proof search, halting closure, or a closed meta-loop classifier. Every accepted consumer route must preserve the displayed packet $P,R,M,A,T,C,G,N$.
\end{theorem}
\begin{proof}
Read the NameCert obligations of \autoref{thm:logic-contradiction-meta-loop-namecert-obligations}. The only content rows are proof pattern, local refutation, open meta-loop refusal, and audit gate; the remaining rows transport, replay, package, and name those same coordinates.

If a consumer asks for quotient collapse, the request is forced through the quotient-soundness refusal surface cited in the obligation proof. If a consumer asks to turn a failed audit item into theorem content, the request is forced through the audit-gate failure witness and remains refusal data.

The carrier supplies no row for total truth, unrestricted choice, global proof search, halting closure, or a closed meta-loop classifier. Therefore every accepted route remains inside $P,R,M,A,T,C,G,N$.
\end{proof}

\begin{theorem}[Logic contradiction meta-loop sibling dependency]
\label{thm:logic-contradiction-meta-loop-sibling-dependency}
The carrier of \autoref{def:logic-contradiction-meta-loop-carrier} is not bijective, row for row, with $\QuotientSoundnessBoundaryUp$, $\AuditGateFailureWitnessUp$, quotient-soundness boundary packets, audit-gate failure packets, MetaCIC decidable-boundary packets, MetaCIC confluence-audit packets, or normal-false-exclusion packets. The present packet jointly carries proof-pattern discipline and open meta-loop refusal, while each sibling exposes only a quotient gate, an audit diagnostic, a checker boundary, a confluence audit, or a local false-exclusion surface.
\end{theorem}
\begin{proof}
Compare first with $\QuotientSoundnessBoundaryUp$. That sibling refuses representative selection and replaces quotient-like reads by displayed $\psame$ transport, but it does not carry the proof-pattern row $P$, the local contradiction row $R$, or the full open meta-loop refusal row $M$.

Compare next with $\AuditGateFailureWitnessUp$. That sibling records a failed gate item, diagnostic readback, refusal target, transport, replay, provenance, and local naming, but it does not carry the quotient-collapse refusal or the proof-pattern discipline as one logic-facing carrier.

The remaining checker and confluence siblings are narrower still. A decidable-boundary packet concerns a checker boundary, a confluence-audit packet concerns rewrite or normalization audit, and a normal-false-exclusion packet concerns one local false-exclusion surface. None contains all rows $P,R,M,A,T,C,G,N$, so no row-preserving bijection can identify it with $\LogicContradictionMetaLoopUp$.
\end{proof}

Later Lean work supplies the $\mathsf{Nontrivial}$ and $\mathsf{FieldFaithful}$ instances for $\LogicContradictionMetaLoopUp$ in $\mathsf{TasteGate.lean}$. Those instances must read the same finite carrier rows $P,R,M,A,T,C,G,N$ and may not add total truth, unrestricted choice, quotient collapse, halting closure, or a closed meta-loop classifier.

\falsifiablePrediction{Any accepted consumer route that reads total truth, choice, quotient collapse, or halting closure without passing through the open meta-loop refusal row refutes the packet.}

\independenceWitness{quotientsoundnessboundary, auditgatefailurewitness, metacicdecidableboundary, metacicconfluenceaudit, normalfalseexclusion: none is bijective because this packet jointly carries proof-pattern discipline and open-meta-loop refusal rather than only one gate or one checker boundary.}

\closureat{LogicContradictionMetaLoopUp}{seedStr}

\begin{closurestatus}{\LogicContradictionMetaLoopUp}
  \constructivestory{A $\LogicContradictionMetaLoopUp$ packet is generated from finite proof-pattern discipline, local-refutation evidence, open meta-loop refusal, audit-gate routing, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:logic-contradiction-meta-loop-carrier}, \autoref{thm:logic-contradiction-meta-loop-namecert-obligations}, \autoref{thm:logic-contradiction-meta-loop-nonescape}, and \autoref{thm:logic-contradiction-meta-loop-sibling-dependency} bind the finite logic/meta-loop carrier and its local NameCert obligation surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close Lean verification, total truth, unrestricted choice, quotient collapse, halting closure, global proof search, or a public standard bridge.}
  \upgradepath{Obligation closure requires checked carrier admission, open meta-loop refusal, audit-gate routing, transport stability, route replay, provenance, local naming, TasteGate instances, and non-escape for the same finite packet.}
\end{closurestatus}
