\chapter{A Concrete Naming Certificate for $\ForwardBindingGapLedgerUp$}
\label{ch:concrete-instances-forward-binding-gap-ledger-namecert}
\origin{ai-composite}

The $\ForwardBindingGapLedgerUp$ packet realizes forward-binding belief as a finite NameCert surface over displayed closed-observation, GAP-boundary, refusal-ledger, apophatic-socket, and belief rows. It is deliberately composite: the carrier assembles the closed observation record of \autoref{ch:concrete-instances-closedobservationsystem-namecert}, the source/refusal boundary of \autoref{ch:concrete-instances-gapclosureboundary-namecert}, the axiom-refusal ledger of \autoref{ch:concrete-instances-axiom-refusal-ledger-namecert}, the socket boundary of \autoref{ch:concrete-instances-apophaticsocket-namecert}, and the observation-update surface of \autoref{ch:concrete-instances-belief-namecert}. Its role is not to present a new atomic TasteGate object, but to package the present commitment row and the visible GAP row that keep future universal-closure use auditable.

\begin{definition}[Forward-binding GAP ledger carrier]
\label{def:forward-binding-gap-ledger-carrier}
A $\ForwardBindingGapLedgerUp$ carrier is a finite $\BHist$ packet
$$
F=(K,R,G,S,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $K$ is the forward-binding commitment row, recording the present use of a universal-closure claim whose witness is not wholly contained in the current record;
\item $R$ is the finite record ledger supplied by the closed-observation surface;
\item $G$ is the GAP socket row that keeps the unsupported universal-closure part visible;
\item $S$ is the noninternalization and refusal row, routing hidden substrate-axiom, hidden induction-principle, and internal-object readings to the displayed refusal surface;
\item $H$ records componentwise $\hsame$ transports for $K,R,G,S$ and for the structural rows;
\item $C$ records the displayed $\Cont$ routes from commitment use to record readback, GAP-socket exposure, refusal readback, and downstream citation;
\item $P$ records $\Pkg$ provenance over $\ClosedObservationSystemUp$, $\GapClosureBoundaryUp$, $\AxiomRefusalLedgerUp$, $\ApophaticSocketUp$, $\BeliefUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\ForwardBindingGapLedgerUp}$ row.
\end{enumerate}
The carrier exports only the finite commitment, record, GAP-socket, refusal, transport, route, provenance, and naming rows. It exports no universal closure, hidden induction principle, substrate axiom, or internal object for $T$.
\end{definition}
\leanchecked{BEDC.Derived.ForwardBindingGapLedgerUp.ForwardBindingGapLedgerTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Forward-binding GAP ledger NameCert obligations]
\label{thm:forward-binding-gap-ledger-namecert-obligations}
For the carrier of \autoref{def:forward-binding-gap-ledger-carrier}, the local $\NameCert_{\ForwardBindingGapLedgerUp}$ surface consists exactly of carrier admission for $F=(K,R,G,S,H,C,P,N)$, forward-binding commitment exposure through $K$, finite record accountability through $R$, GAP-socket preservation through $G$, refusal and noninternalization through $S$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the displayed carrier. The rows $K,R,G,S,H,C,P,N$ are the only rows available to the local certificate.

Read the closed-observation and GAP-boundary siblings. The closed-observation chapter supplies the finite record ledger $R$, while the GAP-boundary chapter keeps a closure request on the displayed source/refusal split rather than on an internal universal-closure row.

Attach the refusal and socket rows. The axiom-refusal and apophatic-socket siblings make unsupported supply visible as a refusal surface, and the belief sibling supplies the present commitment row without changing it into a substrate theorem.

Finally use $H,C,P,N$. These rows transport, replay, package, and name the same finite packet, so the NameCert obligations are exhausted by the displayed route.
\end{proof}

\begin{theorem}[Forward-binding GAP ledger noninternalization]
\label{thm:forward-binding-gap-ledger-noninternalization}
Every accepted $\ForwardBindingGapLedgerUp$ packet keeps the forward-binding commitment outside substrate-internal theoremhood. A downstream consumer may cite $K,R,G,S,H,C,P,N$ as a finite commitment ledger, but it receives no universal closure, hidden induction principle, substrate axiom, hidden theorem, host assumption, or internal object for $T$.
\end{theorem}
\begin{proof}
Begin with the carrier inventory of \autoref{def:forward-binding-gap-ledger-carrier}. The commitment row $K$ is paired with the finite record ledger $R$ and the GAP socket $G$ before any downstream citation can use it.

Use the GAP-boundary refusal surface of \autoref{thm:gap-closure-boundary-namecert-obligations} and \autoref{thm:gap-closure-boundary-refusal-nonescape}. Unsupported closure requests remain on the displayed GAP and refusal rows rather than becoming internal universal closure.

Now apply the axiom-refusal noninternalization theorem, \autoref{thm:axiom-refusal-ledger-noninternalization}. The refusal row $S$ is therefore a visible ledger row, not a consumable axiom or hidden theorem.

The remaining support rows $H,C,P,N$ only preserve that route under transport, replay, provenance, and local naming. Hence a consumer can cite the finite forward-binding ledger but cannot extract an internal object for $T$ or any hidden closure principle from it.
\end{proof}

\begin{theorem}[Forward-binding GAP ledger sibling dependency]
\label{thm:forward-binding-gap-ledger-sibling-dependency}
The $\ForwardBindingGapLedgerUp$ carrier depends on the joint availability of closed-observation records, GAP-boundary refusal, axiom-refusal noninternalization, apophatic-socket exposure, and belief commitment rows. No one sibling among $\ClosedObservationSystemUp$, $\GapClosureBoundaryUp$, $\AxiomRefusalLedgerUp$, $\ApophaticSocketUp$, or $\BeliefUp$ carries all of $K,R,G,S,H,C,P,N$, and no row-preserving reduction to one sibling preserves the local $\NameCert_{\ForwardBindingGapLedgerUp}$ surface.
\end{theorem}
\begin{proof}
Compare first with the closed-observation and belief siblings. $\ClosedObservationSystemUp$ supplies finite record rows, and $\BeliefUp$ supplies observation-update commitment rows, but neither by itself carries the GAP socket and refusal ledger required to keep forward binding noninternal.

Compare next with the GAP-boundary, axiom-refusal, and apophatic-socket siblings. They expose unsupported closure requests, refusal rows, and socket boundaries, but none of them also carries the present commitment row $K$ together with the closed record ledger $R$ and the full structural support $H,C,P,N$.

Thus the chapter is a composite NameCert surface. The dependence on its siblings is visible in the carrier, and the composite packet refuses universal closure, hidden induction, substrate axioms, and internal objects for $T$ precisely because no single sibling row can replace the whole finite route.
\end{proof}

\closureat{ForwardBindingGapLedgerUp}{seedStr}

\begin{closurestatus}{\ForwardBindingGapLedgerUp}
  \constructivestory{A $\ForwardBindingGapLedgerUp$ packet is generated from a forward-binding commitment row, finite closed-observation record ledger, GAP socket, noninternalization and refusal row, componentwise hsame transports, displayed continuation routes, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:forward-binding-gap-ledger-carrier}, \autoref{thm:forward-binding-gap-ledger-namecert-obligations}, \autoref{thm:forward-binding-gap-ledger-noninternalization}, and \autoref{thm:forward-binding-gap-ledger-sibling-dependency} bind the finite composite carrier, NameCert obligations, noninternalization boundary, and sibling dependency surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close universal future cases, export an induction principle, supply a substrate axiom, internalize $T$, assert Lean verification, or bridge to a standard schema.}
  \upgradepath{Obligation closure requires checked carrier admission, record-ledger accountability, GAP-socket preservation, refusal noninternalization, transport stability, route replay, provenance, and local naming for the same finite composite packet.}
\end{closurestatus}
