\chapter{A Concrete Naming Certificate for $\SpinGroupUp$}
\label{ch:concrete-instances-spingroup-namecert}

The Spin-group interface $\SpinGroupUp$ packages the connected double cover of the orthogonal group as a subgroup of the Clifford-algebra units. It depends on $\NameCert_{\CliffordUp}$ (\autoref{ch:concrete-instances-clifford-namecert}) and $\NameCert_{\GroupUp}$ (\autoref{ch:concrete-instances-group-namecert}).

\section{Carrier definition}
\label{sec:spingroup-carrier}

\begin{definition}[SpinGroup root BHist carrier]
\label{def:spingroup-root-bhist-carrier}
The concrete $\SpinGroupUp$ root carrier is the finite $\mathsf{BHist}$ packet whose visible rows are all of the following:
\begin{enumerate}
  \item a carried $\CliffordUp$ endpoint row supplied by $\NameCert_{\CliffordUp}$;
  \item a singleton-history $\GroupUp$ law row supplied by $\NameCert_{\GroupUp}$ for the same visible endpoint shape;
  \item a unit-like Clifford endpoint row, namely a Clifford carrier row classified with the Clifford unit endpoint;
  \item $\Cont$ and $\hsame$ witnesses recording that the displayed multiplication and inverse rows are transported through the Clifford endpoint classifier.
\end{enumerate}
The packet contains no host orthogonal group, no quotient algebra, and no ambient matrix representation; its carrier evidence is exactly the listed $\mathsf{BHist}$, $\Cont$, $\hsame$, $\NameCert$, and $\mathsf{UnaryHistory}$ data.
\end{definition}

\begin{theorem}[SpinGroup source scope]
\label{thm:spingroup-root-carrier-source-scope}
Every row of \autoref{def:spingroup-root-bhist-carrier} is sourced through $\NameCert_{\CliffordUp}$ or $\NameCert_{\GroupUp}$. The Clifford endpoint, unit-like endpoint, product transport, and inverse transport rows are read from the Clifford certificate; the singleton-history associativity, unit, and inverse law rows are read from the group certificate over $\mathsf{UnaryHistory}$. No additional source row is admitted by the $\SpinGroupUp$ root carrier.
\end{theorem}
\begin{proof}
Unpack the root carrier packet. Each constructor in the packet names either a Clifford carrier row, a Clifford classifier row, a group singleton-history law row, or a transport witness connecting these rows.

The Clifford rows are discharged by the carrier, unit, product, and classifier clauses of $\NameCert_{\CliffordUp}$. The group law rows are discharged by the singleton-history law surface of $\NameCert_{\GroupUp}$, with the visible endpoint supplied by the same $\mathsf{UnaryHistory}$ spine.

It remains only to account for the transport witnesses. These are ordinary $\Cont$ and $\hsame$ rows whose endpoints are already present in the two certificates, so repacking them adds no third source.
\end{proof}

\begin{theorem}[Clifford unit lift for SpinGroup]
\label{thm:spingroup-root-clifford-unit-lift}
If a $\CliffordUp$ carrier row is classified with the Clifford unit endpoint, then the same row lifts to the $\SpinGroupUp$ root carrier by pairing it with the singleton $\GroupUp$ identity law row and the reflexive $\Cont$ and $\hsame$ transport witnesses. The lift preserves the visible Clifford endpoint classifier and records the row as unit-like inside the SpinGroup packet.
\end{theorem}
\begin{proof}
Start with the displayed Clifford carrier row and its classifier witness to the unit endpoint. The carrier clause of $\NameCert_{\CliffordUp}$ supplies the endpoint row, while classifier reflexivity supplies the stable unit comparison needed by the packet.

Next choose the singleton-history identity row from $\NameCert_{\GroupUp}$. Since the endpoint spine is the same unary history, the group row and the Clifford unit row share the visible boundary required by the root carrier.

Finally repack the Clifford row, the singleton identity law, and the reflexive $\Cont$ and $\hsame$ witnesses into \autoref{def:spingroup-root-bhist-carrier}. No multiplication or inverse row is consumed in this special case.
\end{proof}

\begin{theorem}[SpinGroup group-law transport]
\label{thm:spingroup-root-group-law-transport}
Let $a$, $b$, $a'$, and $b'$ be $\SpinGroupUp$ root-carrier rows whose Clifford endpoints are classified by the $\CliffordUp$ endpoint classifier and whose group-law rows are singleton-history $\GroupUp$ rows. If $\hsame(a,a')$ and $\hsame(b,b')$ hold through the Clifford classifier, then multiplication and inverse rows transported by $\Cont$ remain inside the $\SpinGroupUp$ root carrier and carry the corresponding $\GroupUp$ multiplication and inverse laws.
\end{theorem}
\begin{proof}
Unpack the two root-carrier rows. The Clifford parts expose carried endpoints and classifier witnesses, while the group parts expose the singleton-history multiplication and inverse law rows.

For multiplication, compose the two Clifford endpoint transports with the Clifford product transport supplied by $\NameCert_{\CliffordUp}$. The group singleton-history multiplication row is then read through $\NameCert_{\GroupUp}$ and placed over the transported endpoint.

For inverse, use the same endpoint classifier transport with the Clifford inverse endpoint row. The singleton-history inverse law supplies the group side, and the $\Cont$ witness repacks the result as a root-carrier inverse row.

The final packet is again of the form in \autoref{def:spingroup-root-bhist-carrier}: the visible Clifford endpoint has moved only by $\hsame$, and every group-law row remains a $\GroupUp$ row over the same unary history.
\end{proof}

\begin{theorem}[SpinGroup NameCert obligation surface]
\label{thm:spingroup-root-namecert-obligation-surface}
The rows in \autoref{def:spingroup-root-bhist-carrier}, together with \autoref{thm:spingroup-root-carrier-source-scope}, \autoref{thm:spingroup-root-clifford-unit-lift}, and \autoref{thm:spingroup-root-group-law-transport}, form the $\SpinGroupUp$ root $\NameCert$ obligation surface. The surface consists precisely of Clifford source scope, unit lift, multiplication transport, inverse transport, singleton-history group laws, and finite ledger exactness for these rows.
\end{theorem}
\begin{proof}
Read the obligation surface row by row. Source scope is supplied by \autoref{thm:spingroup-root-carrier-source-scope}; the unit face is supplied by \autoref{thm:spingroup-root-clifford-unit-lift}; multiplication and inverse transport are supplied by \autoref{thm:spingroup-root-group-law-transport}.

The classifier side is finite because every row is a named component of the carrier packet. Inverting a proposed $\SpinGroupUp$ root obligation therefore yields either a Clifford carrier/classifier row, a singleton-history $\GroupUp$ law row, or a displayed $\Cont$ or $\hsame$ witness between those endpoints.

Repacking these cases gives the stated root $\NameCert$ surface. No Spin or Pin global presentation, orthogonal action, matrix model, or host quotient algebra is used by this obligation surface.
\end{proof}

\section{The certificate}
\label{sec:spingroup-certificate}

\begin{theorem}[SpinGroup carrier obligation]\label{thm:spingroup-carrier-obligation}
A $\SpinGroupUp$ certificate carries its object row as a $\mathsf{BHist}$ predicate over Clifford-even lift rows, rotation/projection endpoint rows, and a source row supplied by $\NameCert_{\CliffordUp}$. The carrier is not a host spin group: every admitted spin row is a finite BEDC packet whose visible fields are a Clifford carrier row, an even-parity $\mathsf{UnaryHistory}$ ledger, a product-unit row, and a projection row into the already certified orthogonal surface.
\end{theorem}
\begin{proof}
Read the carrier slot of the roadmap ten-field template. The traditional target is a spin lift, but the BEDC source is the $\NameCert_{\CliffordUp}$ row together with the group operation rows named by $\NameCert_{\GroupUp}$.

The $\mathsf{BHist}$ carrier predicate therefore accepts exactly the finite Clifford lift packet, the even-parity $\mathsf{UnaryHistory}$ ledger, and the projection endpoint row. The projection is read by $\Cont$ from the lift packet to the rotation endpoint, while $\hsame$ supplies only classifier transport between carried representatives.

No host spin group is introduced. The certificate surface exports the rows named by the $\NameCert$ dependencies and the displayed BEDC ledgers, so any downstream carrier use must project through those rows.
\end{proof}

\begin{theorem}[SpinGroup classifier obligation]\label{thm:spingroup-classifier-obligation}
Two $\SpinGroupUp$ carrier rows are classified exactly when their Clifford lift rows, double-cover projection rows, and even-Clifford ledger rows are compared by $\hsame$ in the same $\mathsf{BHist}$ scope. The classifier is componentwise over the lift, projection, and parity ledger; it does not identify two rows by appealing to an external Lie-group equality.
\end{theorem}
\begin{proof}
Use the classifier field of the roadmap ten-field template after \autoref{thm:spingroup-carrier-obligation} has fixed the carried rows. The source classifier comes from $\NameCert_{\CliffordUp}$, and the visible projection endpoint is a $\mathsf{BHist}$ row, so the only available comparison is $\hsame$.

For two carrier packets, project their Clifford lift rows, their projection rows, and their even-parity $\mathsf{UnaryHistory}$ ledgers. Componentwise $\hsame$ on these three rows is stable under the $\NameCert$ transport fields, and the $\Cont$ projection row keeps the lift endpoint attached to the same public rotation surface.

Conversely, any classifier row for $\SpinGroupUp$ must be readable through these same projections, because the carrier has no additional equality field. Hence the displayed componentwise comparison is the whole classifier obligation.
\end{proof}

\begin{theorem}[SpinGroup lift parity ledger]\label{thm:spingroup-lift-parity-ledger}
The hidden ledger of a $\SpinGroupUp$ certificate records two rows: the even-Clifford parity row as $\mathsf{UnaryHistory}$ data over $\mathsf{BHist}$ words, and the two-to-one projection row as $\Cont$ data from the Clifford lift to the orthogonal endpoint. These rows are ledger data of the certificate, not new public carrier primitives.
\end{theorem}
\begin{proof}
Project the ledger field of the roadmap ten-field template. The Clifford source supplies word histories and product rows, while the spin certificate adds the parity and projection ledgers needed to read a lift as a double-cover point.

The parity row is unary because it records the even length of the Clifford word presentation. It is scoped as $\mathsf{UnaryHistory}$ over $\mathsf{BHist}$ rather than as an ambient integer parity predicate, and $\hsame$ transport is inherited from the Clifford word classifier.

The projection row is a $\Cont$ witness from the lift packet to the rotation endpoint. It is hidden ledger data because it witnesses how the public orthogonal row is read from the lift, while the public boundary remains the projection endpoint itself.
\end{proof}

\begin{theorem}[SpinGroup concrete lift closure]\label{thm:spingroup-concrete-lift-closure}
If two admitted $\SpinGroupUp$ lift rows are composable through the Clifford product ledger, then $\Cont$-composition of the two lift packets preserves the carrier and transports the classifier. The resulting packet has a Clifford-even lift row, a composed projection row, and a transported even-parity ledger in the same $\mathsf{BHist}$ certificate scope.
\end{theorem}
\begin{proof}
Unpack the operation and stability fields of the roadmap ten-field template. Each input lift is already a $\mathsf{BHist}$ packet with a Clifford carrier row, an even $\mathsf{UnaryHistory}$ ledger, and a projection row.

Compose the lift packets using the Clifford product continuation supplied by $\NameCert_{\CliffordUp}$. The two even-parity ledgers compose to another even ledger inside the same unary history scope, and the two projection rows compose by $\Cont$ to the corresponding orthogonal endpoint.

Classifier transport is componentwise. The lift comparison is transported by the Clifford $\NameCert$ classifier, the projection comparison by the composed $\Cont$ rows, and the parity comparison by $\hsame$ on the unary ledger. These are exactly the carrier fields of \autoref{thm:spingroup-carrier-obligation}.
\end{proof}

\begin{theorem}[SpinGroup spin double cover boundary]\label{thm:spingroup-spin-double-cover-boundary}
The public boundary of $\SpinGroupUp$ is the double-cover projection row from a Clifford-even lift to the already certified orthogonal or special-orthogonal surface. The boundary is a $\mathsf{BHist}$ projection ledger classified by $\hsame$ and transported by $\Cont$; it is not an external Lie group supplied outside the BEDC certificate.
\end{theorem}
\begin{proof}
Read the exactness and boundary fields of the roadmap ten-field template. The carrier and ledger obligations have already fixed the Clifford lift, the even $\mathsf{UnaryHistory}$ row, and the projection endpoint as the complete visible surface.

The public row is therefore the projection endpoint, together with its $\Cont$ witness from the Clifford-even lift. The orthogonal or special-orthogonal target is already certified by its own $\NameCert$ row, so $\SpinGroupUp$ exports only the double-cover boundary into that surface.

Exactness runs in the reverse direction. Any public spin-boundary use must recover the lift row, parity ledger, and projection continuation from the same $\mathsf{BHist}$ packet; rows outside those fields are not part of this certificate.
\end{proof}

\begin{theorem}[SpinGroupUp Clifford unit carrier obligation]
\label{thm:spingroup-clifford-unit-carrier-obligation}
A $\SpinGroupUp$ carrier is a $\mathsf{BHist}$ packet whose visible rows are a
$\CliffordUp$ unit row, an orthogonal-action endpoint row, and a $\GroupUp$
carrier row. The packet exports no host Lie group, matrix equality, or ambient
Clifford algebra equality beyond the displayed BEDC rows.
\end{theorem}
\begin{proof}
Use the dependency surface stated at the start of this chapter. The
$\CliffordUp$ certificate supplies the unit row inside the Clifford-algebra
interface, while the $\GroupUp$ certificate supplies the public group-carrier
row read by downstream group consumers.

The $\SpinGroupUp$ carrier is the ten-field certificate packet that places
those two dependency rows beside the orthogonal-action endpoint row. Since the
carrier is a $\mathsf{BHist}$ packet, all equality and transport visible at the
interface is through $\hsame$ and the named classifier rows, not through a host
matrix or Lie-group equality.
\end{proof}

\begin{theorem}[SpinGroupUp double-cover ledger obligation]
\label{thm:spingroup-double-cover-ledger-obligation}
The double-cover ledger for a $\SpinGroupUp$ packet records the Clifford unit
endpoint, the projected orthogonal-action endpoint, and the kernel-sign witness
as $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\Pkg$ rows. No additional covering
space, topology, or host quotient is exported as public carrier data.
\end{theorem}
\begin{proof}
Read the same dependency rows through the $\NameCert$ ten-field template. The
$\CliffordUp$ side contributes the unit endpoint, and the projected
orthogonal-action endpoint records the public target of the double-cover map.

The kernel-sign witness is ledger data: it is carried by BEDC rows using
$\mathsf{BHist}$ endpoints, $\hsame$ transport, continuation provenance
$\Cont$, and package evidence $\Pkg$. Repacking those rows into the ledger slot
of the $\SpinGroupUp$ certificate yields the stated double-cover ledger without
adding a host quotient or topological covering object.
\end{proof}

\begin{theorem}[SpinGroupUp group interface boundary]
\label{thm:spingroup-group-interface-boundary}
Any $\GroupUp$ consumer of a displayed $\SpinGroupUp$ packet may read only the
multiplication, identity, inverse, and classifier rows supplied by that packet.
The Clifford multiplication rows, orthogonal projection rows, and kernel-sign
witness remain ledger rows and are not exported as extra group operations.
\end{theorem}
\begin{proof}
Project the $\GroupUp$ dependency from the carrier packet described in
\autoref{thm:spingroup-clifford-unit-carrier-obligation}. The public group
interface consists of its multiplication, identity, inverse, and classifier
rows, all carried through the same $\mathsf{BHist}$ packet.

The double-cover data is read separately through
\autoref{thm:spingroup-double-cover-ledger-obligation}. It supplies provenance
for why the group rows come from Clifford units and the orthogonal projection,
but it stays in the ledger slot of the ten-field $\NameCert$ template. Thus a
$\GroupUp$ consumer receives exactly the group interface and no hidden Clifford
or projection operation.
\end{proof}

\begin{theorem}[SpinGroupUp Clifford-unit source obligation]
\label{thm:spingroup-clifford-unit-source-obligation}
A $\SpinGroupUp$ source row is a displayed $\CliffordUp$ unit endpoint together
with even-product provenance, a $\GroupUp$ multiplication row, and
$\mathsf{BHist}$, $\Cont$, and $\mathsf{Pkg}$ ledgers tying the unit read and
the product read to the same carried source. The row records multiplication
and inverse access only through the inherited Clifford-unit and group
certificates, and it does not assert an uncarried host-level spin subgroup.
\end{theorem}
\begin{proof}
Read the Clifford dependency as a unit endpoint in the $\CliffordUp$ carrier.
The even-product provenance is a finite $\mathsf{BHist}$ ledger whose factors
are carried Clifford generators and whose product endpoint is the displayed
unit row.

Read the group dependency as the multiplication and inverse package on those
unit endpoints. The $\GroupUp$ row supplies the operation laws only for the
displayed carried endpoints, while $\Cont$ records the product computation and
$\mathsf{Pkg}$ records the shared provenance.

Combining the two dependency reads gives the $\SpinGroupUp$ source row. Every
field is inherited from $\CliffordUp$, $\GroupUp$, $\mathsf{BHist}$, $\Cont$,
and $\mathsf{Pkg}$, so no ambient subgroup predicate or external Clifford
algebra quotient is added.
\end{proof}

\begin{theorem}[SpinGroupUp double-cover fiber classifier]
\label{thm:spingroup-double-cover-fiber-classifier}
The double-cover classifier for $\SpinGroupUp$ compares two carried spin
endpoints by their Clifford-unit carrier rows together with the shared
$\mathsf{OrthogonalGroup}^{\uparrow}$ action endpoint. Two spin rows are in the same fiber
exactly when the Clifford-unit comparisons and the displayed orthogonal-action
readback agree in the package ledger; the classifier does not quotient by
host-level signs or by an unrecorded kernel object.
\end{theorem}
\begin{proof}
Unpack two $\SpinGroupUp$ source rows using
\autoref{thm:spingroup-clifford-unit-source-obligation}. Each row exposes a
carried Clifford unit, even-product provenance, multiplication and inverse
rows, and package provenance.

Compare the Clifford-unit coordinates with the inherited $\CliffordUp$
classifier. Then compare the displayed orthogonal-action endpoint using the
shared action readback recorded in the same $\mathsf{Pkg}$ ledger.

The fiber classifier is the conjunction of these displayed comparisons. Since
the sign ambiguity is represented only by carried Clifford-unit rows and their
action endpoint, the construction never forms a host sign quotient or an
unrecorded double-cover kernel.
\end{proof}

\begin{theorem}[SpinGroupUp group consumer boundary]
\label{thm:spingroup-group-consumer-boundary}
Downstream $\LieGroupUp$ or $\PinGroupUp$ consumers of $\SpinGroupUp$ may read
only the Clifford unit row, multiplication and inverse rows, the double-cover
classifier of \autoref{thm:spingroup-double-cover-fiber-classifier}, and
$\NameCert$ provenance. They may not inspect a host Lie group, a host sign
quotient, or an uncarried Clifford algebra carrier outside the displayed BEDC
source package.
\end{theorem}
\begin{proof}
The source obligation exposes the carried unit and the group operation rows.
These are sufficient for group-style consumers to read multiplication,
inverse, identity provenance, and the finite even-product ledger.

The double-cover classifier exposes exactly the additional fiber data used by
geometry consumers: the Clifford-unit comparison and the shared orthogonal
action endpoint. The consumer therefore reads a package of named
$\mathsf{BHist}$ rows, not an ambient quotient.

The $\NameCert$ provenance binds these rows to the $\SpinGroupUp$ interface.
Any $\LieGroupUp$ or $\PinGroupUp$ consumer that needs more structure must add
its own displayed source rows rather than reading an unrecorded host object
through this boundary.
\end{proof}
