\chapter{A Concrete Naming Certificate for $\TraditionRegistryUp$}
\label{ch:concrete-instances-tradition-registry-namecert}
\origin{ai}

The $\TraditionRegistryUp$ packet realizes the tradition registry of \autoref{subsec:philosophy-tradition-registry-table} as a finite NameCert carrier. It sits after the auditable-generativity context of \autoref{ch:visions-philosophy-auditable-generativity}, beside the core registry index of \autoref{ch:concrete-instances-core-registry-index-namecert}, the concept-registry surface of \autoref{ch:concrete-instances-concept-registry-surface-namecert}, and the theorem-gap registry of \autoref{ch:concrete-instances-theoremgapregistry-namecert}. These siblings index concepts, expose concept surfaces, and record theorem gaps; the present packet binds one inherited tradition comparison to the rejected-surplus and comparison-discipline rows required before that comparison is named.

\begin{definition}[Tradition registry carrier]
\label{def:tradition-registry-carrier}
A $\TraditionRegistryUp$ carrier is a finite $\BHist$ packet
$$
X=(T,S,P,R,H,C,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the tradition row, naming the inherited tradition and the traditional claim being compared.
\item $S$ is the BEDC-site row, naming the concrete BEDC chapter, definition, theorem, or registry surface where the comparison is allowed to land.
\item $P$ is the preserved-structure row, recording the exact constructor, classifier, transport, or obligation shape preserved by the comparison.
\item $R$ is the rejected-surplus row, recording the doctrine, host semantics, prose reading, metaphysical claim, or ambient assumption not imported into the BEDC site.
\item $H$ records componentwise $\hsame$ transport for the tradition, site, preserved-structure, rejected-surplus, continuation, provenance, and naming rows.
\item $C$ records the displayed $\Cont$ route from the inherited comparison through the BEDC site and rejected-surplus boundary.
\item $Q$ is the $\Pkg$ provenance row over philosophy tradition entries, $\CoreRegistryIndexUp$, $\ConceptRegistrySurfaceUp$, $\TheoremGapRegistryUp$, $\ClaimRegistryLayerUp$, $\AuditSystemUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\TraditionRegistryUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through $T,S,P,R,H,C,Q,N$. It has no coordinate for inherited doctrine without rejected surplus, a BEDC site without preserved structure, a hidden comparison rule, or a sibling registry bijection.
\end{definition}
\leandef{BEDC.Derived.TraditionRegistryUp.TraditionRegistryUp}

\begin{theorem}[Tradition registry NameCert obligations]
\label{thm:tradition-registry-namecert-obligations}
For the carrier of \autoref{def:tradition-registry-carrier}, the local $\NameCert_{\TraditionRegistryUp}$ surface consists exactly of carrier admission for $X=(T,S,P,R,H,C,Q,N)$, tradition and BEDC-site exposure through $T,S$, preserved-structure exposure through $P$, rejected-surplus exposure through $R$, componentwise transport through $H$, displayed comparison replay through $C$, package provenance through $Q$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite carrier. The rows $T,S,P,R$ display the inherited tradition, the BEDC landing site, the structure preserved by the comparison, and the surplus reading rejected at that site.

The support rows $H,C,Q,N$ then transport, replay, source, and name the same comparison packet. They do not add a second doctrine row, a second landing site, or an unrecorded comparison rule.

Thus every accepted NameCert obligation is one of the displayed rows. Since the carrier contains no further coordinate, the listed rows exhaust the local $\NameCert_{\TraditionRegistryUp}$ surface.
\end{proof}

\begin{theorem}[Tradition registry rejected-surplus nonescape]
\label{thm:tradition-registry-rejected-surplus-nonescape}
Every accepted $\TraditionRegistryUp$ packet must display the rejected-surplus row $R$ before a tradition comparison can be exported as a BEDC comparison. A packet with $T,S,P,H,C,Q,N$ but no $R$ is outside the registry surface.
\end{theorem}
\begin{proof}
Use the obligation surface of \autoref{thm:tradition-registry-namecert-obligations}. It requires the preserved structure and the rejected surplus to be displayed in the same finite packet before the local name is public.

The siblings named by the provenance row can index a concept, expose a concept surface, record a theorem gap, route a claim, or audit the packet. None of them manufactures the missing rejected-surplus coordinate.

Therefore an export without $R$ is not an accepted $\TraditionRegistryUp$ packet. It has left the finite registry carrier rather than completing it.
\end{proof}

\begin{theorem}[Tradition registry sibling dependency]
\label{thm:tradition-registry-sibling-dependency}
The sibling packets $\CoreRegistryIndexUp$, $\ConceptRegistrySurfaceUp$, $\TheoremGapRegistryUp$, $\ClaimRegistryLayerUp$, and $\AuditSystemUp$ are dependencies of $\TraditionRegistryUp$ only through the displayed provenance and replay rows $Q,C$. None is bijective with the carrier $X=(T,S,P,R,H,C,Q,N)$.
\end{theorem}
\begin{proof}
Read the carrier coordinates. The tradition row, BEDC-site row, preserved-structure row, and rejected-surplus row are local to $X$ and are not replaced by a concept index, theorem-gap row, claim row, or audit row.

The siblings enter through $Q$ as package provenance and through $C$ as displayed replay. Those rows state where the comparison can be checked and consumed, but they do not erase $T,S,P,R$ or reconstruct them from a sibling alone.

Hence each sibling is a non-bijective dependency. The registry packet remains the finite tradition-comparison surface with its own rejected-surplus and naming rows.
\end{proof}

\falsifiablePrediction{Any accepted TraditionRegistryUp packet without a rejected-surplus row is rejected before the comparison can be exported as a BEDC tradition-registry entry.}

\independenceWitness{coreregistryindex, conceptregistrysurface, theoremgapregistry, claimregistrylayer, auditsystem: no sibling is bijective because each exposes only an index, concept surface, theorem-gap row, claim route, or audit route, while TraditionRegistryUp binds tradition, BEDC site, preserved structure, rejected surplus, hsame transport, Cont replay, Pkg provenance, and local NameCert in one packet.}

The later Lean \texttt{TasteGate.lean} for this chapter must include explicit \texttt{Nontrivial TraditionRegistryUp} and \texttt{FieldFaithful TraditionRegistryUp} instances preserving $T,S,P,R,H,C,Q,N$ as separate displayed rows.

\closureat{TraditionRegistryUp}{seedStr}

\begin{closurestatus}{\TraditionRegistryUp}
  \constructivestory{A $\TraditionRegistryUp$ packet is generated from tradition, BEDC-site, preserved-structure, rejected-surplus, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:tradition-registry-carrier}, \autoref{thm:tradition-registry-namecert-obligations}, \autoref{thm:tradition-registry-rejected-surplus-nonescape}, and \autoref{thm:tradition-registry-sibling-dependency} bind tradition comparisons to a finite rejected-surplus NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, philosophical correctness of every tradition comparison, or completeness of the sibling registry lattice.}
  \upgradepath{Lean closure requires Nontrivial TraditionRegistryUp and FieldFaithful TraditionRegistryUp instances in \texttt{lean4/BEDC/Derived/TraditionRegistryUp/TasteGate.lean}.}
\end{closurestatus}
