\chapter{A Concrete Naming Certificate for $\TraditionComparisonBoundaryUp$}
\label{ch:concrete-instances-tradition-comparison-boundary-namecert}
\origin{ai}

The $\TraditionComparisonBoundaryUp$ packet realizes the structural-comparison discipline of \autoref{sec:visions-philosophy-traditions} as a finite NameCert boundary. It sits beside the claim registry layer of \autoref{ch:concrete-instances-claimregistrylayer-namecert}, the cannot-claim registry of \autoref{ch:concrete-instances-axiszeckendorfcannotclaim-namecert}, the object-knowledge certificate of \autoref{ch:concrete-instances-objectknowledgecertificate-namecert}, and the registry export consistency gate of \autoref{ch:concrete-instances-registry-export-consistency-gate-namecert}. Those siblings regulate claim export, refusal rows, object-knowledge licensing, and registry consistency; this packet binds tradition source, BEDC landing, rejected surplus, and structural distinction before any comparison may be exported.

\begin{definition}[Tradition comparison boundary carrier]
\label{def:tradition-comparison-boundary-carrier}
A $\TraditionComparisonBoundaryUp$ carrier is a finite $\BHist$ packet
$$
T=(S,L,R,D,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the tradition-source row, recording the inherited tradition, text family, question, vocabulary surface, and comparison prompt.
\item $L$ is the BEDC landing row, recording the carrier, relation, classifier, ledger, certificate, gap, or $T$-position onto which the structural core lands.
\item $R$ is the rejected-surplus row, recording the doctrinal, metaphysical, host-semantic, or identity claim not imported by the comparison.
\item $D$ is the structural-distinction row, recording that the accepted comparison preserves a structural landing while refusing doctrinal identity.
\item $H$ stores componentwise $\hsame$ transport for source, landing, rejected-surplus, distinction, replay, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay for the comparison route from source row through landing row and rejected-surplus inspection.
\item $P$ is the $\Pkg$ provenance over $\TraditionComparisonBoundaryUp$, $\ClaimRegistryLayerUp$, $\AxisZeckendorfCannotClaimUp$, $\ObjectKnowledgeCertificateUp$, $\RegistryExportConsistencyGateUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\TraditionComparisonBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for tradition membership alone, inherited doctrinal truth, host-semantic identity, or comparison export outside the displayed packet $T=(S,L,R,D,H,C,P,N)$.
\end{definition}

\begin{definition}[Tradition comparison boundary classifier]
\label{def:tradition-comparison-boundary-classifier}
The $\TraditionComparisonBoundaryUp$ classifier accepts exactly those packets of \autoref{def:tradition-comparison-boundary-carrier} whose comparison is read only through the structural landing row $L$ together with the rejected-surplus row $R$. The classifier does not compare traditions by doctrinal identity, inherited vocabulary, host truth, or prose affinity unless those readings are rejected by $R$ and kept outside the accepted landing.
\end{definition}

\begin{theorem}[Tradition comparison boundary NameCert obligations]
\label{thm:tradition-comparison-boundary-namecert-obligations}
For the carrier of \autoref{def:tradition-comparison-boundary-carrier}, the local $\NameCert_{\TraditionComparisonBoundaryUp}$ surface consists exactly of carrier admission for $T=(S,L,R,D,H,C,P,N)$; tradition-source exposure through $S$; BEDC landing exposure through $L$; rejected-surplus exposure through $R$; structural-distinction exactness through $D$; componentwise transport through $H$; displayed replay through $C$; package provenance through $P$; and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.TraditionComparisonBoundaryUp.TraditionComparisonBoundaryTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the finite packet of \autoref{def:tradition-comparison-boundary-carrier}. Row $S$ displays the inherited source, while row $L$ displays the exact BEDC landing surface available to the comparison.

The rejected-surplus row $R$ and the structural-distinction row $D$ are then read together. By the classifier of \autoref{def:tradition-comparison-boundary-classifier}, acceptance depends on structural landing and rejected surplus, so a doctrinal or host-semantic identity claim has no accepted coordinate.

Finally $H,C,P,N$ transport, replay, package, and name the same packet. Since no additional row can export tradition membership, inherited doctrine, or prose affinity as a BEDC identity, the listed rows exhaust the local $\NameCert_{\TraditionComparisonBoundaryUp}$ surface.
\end{proof}

\begin{theorem}[Tradition comparison boundary rejects doctrinal identity]
\label{thm:tradition-comparison-boundary-no-doctrinal-identity}
No accepted $\TraditionComparisonBoundaryUp$ packet exports doctrinal identity between an inherited tradition and a BEDC object. Every accepted comparison must display both the BEDC landing row $L$ and the rejected-surplus row $R$ in the same carrier.
\end{theorem}
\begin{proof}
Let an accepted packet be
$$
T=(S,L,R,D,H,C,P,N).
$$
The classifier of \autoref{def:tradition-comparison-boundary-classifier} reads the packet only through $L$ and $R$ for comparison acceptance.

If a route exports doctrinal identity, it must either bypass $R$ or treat $R$ as empty surplus. Both moves leave the displayed carrier of \autoref{def:tradition-comparison-boundary-carrier}: $R$ is the row that records what is not imported by the comparison.

The structural-distinction row $D$ records that the comparison preserves a landing without identifying the tradition with the BEDC object. Transport, replay, package provenance, and naming rows preserve that packet; they do not add a doctrinal-identity coordinate.
\end{proof}

\begin{theorem}[Tradition comparison boundary sibling independence]
\label{thm:tradition-comparison-boundary-sibling-independence}
The $\TraditionComparisonBoundaryUp$ carrier is not bijective, under NameCert-row preservation, to $\ClaimRegistryLayerUp$, $\AxisZeckendorfCannotClaimUp$, $\ObjectKnowledgeCertificateUp$, or $\RegistryExportConsistencyGateUp$.
\end{theorem}
\begin{proof}
Compare the displayed rows. $\ClaimRegistryLayerUp$ regulates package-level claim export, $\AxisZeckendorfCannotClaimUp$ records cannot-claim refusal, $\ObjectKnowledgeCertificateUp$ licenses object knowledge, and $\RegistryExportConsistencyGateUp$ checks registry export consistency.

None of those sibling packets carries the tradition-source row $S$, BEDC landing row $L$, rejected-surplus row $R$, structural-distinction row $D$, and local $\NameCert_{\TraditionComparisonBoundaryUp}$ row $N$ in one finite comparison packet.

A NameCert-row-preserving bijection would have to preserve those rows as a joint comparison boundary. Since each sibling lacks at least one of the source, landing, surplus, or distinction coordinates, no such bijection exists.
\end{proof}

\falsifiablePrediction{If a comparison route exports doctrinal identity without a rejected-surplus row, it is not an accepted TraditionComparisonBoundaryUp packet.}

\independenceWitness{claimregistrylayer, axiszeckendorfcannotclaim, objectknowledgecertificate, registryexportconsistencygate: none carries the tradition-source, BEDC landing, rejected-surplus, structural-distinction, and local NameCert rows in one packet.}

The Lean follow-up must provide $\Nontrivial\ \TraditionComparisonBoundaryUp$ and $\FieldFaithful\ \TraditionComparisonBoundaryUp$ instances in \texttt{lean4/BEDC/Derived/TraditionComparisonBoundaryUp/TasteGate.lean}. Those instances must preserve $S,L,R,D,H,C,P,N$ as separate displayed rows before $\mathsf{BEDC.Derived.TraditionComparisonBoundaryUp.TraditionComparisonBoundaryTasteGate\_single\_carrier\_alignment}$ may be cited by a checked paper marker.

\closureat{TraditionComparisonBoundaryUp}{seedStr}
\closureat{TraditionComparisonBoundaryUp}{obligationStr}

\begin{closurestatus}{\TraditionComparisonBoundaryUp}
  \constructivestory{A $\TraditionComparisonBoundaryUp$ packet is generated from tradition-source, BEDC landing, rejected-surplus, structural-distinction, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:tradition-comparison-boundary-carrier}, \autoref{def:tradition-comparison-boundary-classifier}, \autoref{thm:tradition-comparison-boundary-namecert-obligations}, \autoref{thm:tradition-comparison-boundary-no-doctrinal-identity}, and \autoref{thm:tradition-comparison-boundary-sibling-independence} bind structural tradition comparison to a finite NameCert boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, public export closure, or the correctness of any inherited tradition's doctrine.}
  \upgradepath{Lean closure requires Nontrivial TraditionComparisonBoundaryUp and FieldFaithful TraditionComparisonBoundaryUp instances in \texttt{lean4/BEDC/Derived/TraditionComparisonBoundaryUp/TasteGate.lean}.}
\end{closurestatus}
