\chapter{A Concrete Naming Certificate for $\TraditionScienceRegistryBridgeUp$}
\label{ch:concrete-instances-tradition-science-registry-bridge-namecert}
\origin{ai}

The $\TraditionScienceRegistryBridgeUp$ packet realizes the tradition and science registry rows of \autoref{subsec:philosophy-tradition-registry-table} and \autoref{subsec:philosophy-science-registry-table} as one finite NameCert carrier. It sits beside the auditable-generativity package of \autoref{ch:visions-philosophy-auditable-generativity}, the concept-registry surface of \autoref{ch:concrete-instances-concept-registry-surface-namecert}, the core registry index of \autoref{ch:concrete-instances-core-registry-index-namecert}, the registry layer of \autoref{ch:concrete-instances-registrylayer-namecert}, and the claim registry layer of \autoref{ch:concrete-instances-claimregistrylayer-namecert}. Those siblings expose concept, index, registry, claim, or export rows; this packet binds tradition comparison and science failure-surface rows in one carrier before either family can be exported as package prose.

\begin{definition}[Tradition and science registry bridge carrier]
\label{def:tradition-science-registry-bridge-carrier}
A $\TraditionScienceRegistryBridgeUp$ carrier is a finite $\BHist$ packet
$$
Q=(T,P,R,S,E,F,H,C,K,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $T$ is the tradition-entry row, recording tradition, traditional claim, BEDC site, preserved structure, rejected surplus, and status.
\item $P$ is the preserved-structure row, recording the exact structural feature allowed to pass from the inherited tradition into the BEDC site.
\item $R$ is the rejected-surplus row, recording the metaphysical, doctrinal, host-semantic, or prose-only reading that is not imported by the comparison.
\item $S$ is the science-entry row, recording name, records carrier, invariant carrier, prediction gap, bridge status, claim status, and science-roadmap boundary.
\item $E$ is the empirical-ledger row, recording the displayed records, measurement route, model-facing ledger, or explicit absence of empirical support for the same science entry.
\item $F$ is the failure-surface row, recording what would block promotion of the science entry, including missing source rows, unledgered measurement, hidden choice, quotient collapse, propositional extensionality, missing invariant, or missing empirical ledger.
\item $H$ stores componentwise $\hsame$ transport for tradition entry, preserved structure, rejected surplus, science entry, empirical ledger, failure surface, replay, provenance, and local naming rows.
\item $C$ is the displayed $\Cont$ replay row through the tradition-comparison and science-failure routes.
\item $K$ is the $\Pkg$ provenance over $\ConceptRegistrySurfaceUp$, $\CoreRegistryIndexUp$, $\RegistryLayerUp$, $\ClaimRegistryLayerUp$, $\RegistryExportSurfaceUp$, philosophy tradition registry rows, philosophy science registry rows, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\TraditionScienceRegistryBridgeUp}$ row.
\end{enumerate}
The carrier has no coordinate for inherited vocabulary without rejected surplus, scientific roadmap prose without a failure surface, empirical claims without a ledger row, or registry export outside the displayed packet $Q=(T,P,R,S,E,F,H,C,K,N)$.
\end{definition}

\begin{theorem}[Tradition and science registry bridge obligations]
\label{thm:tradition-science-registry-bridge-obligations}
For the carrier of \autoref{def:tradition-science-registry-bridge-carrier}, the local $\NameCert_{\TraditionScienceRegistryBridgeUp}$ surface consists exactly of carrier admission for $Q=(T,P,R,S,E,F,H,C,K,N)$; tradition-comparison exposure through $T,P,R$; science-roadmap exposure through $S,E,F$; componentwise transport through $H$; displayed replay through $C$; package provenance through $K$; and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.TraditionScienceRegistryBridgeUp.TraditionScienceRegistryBridgeTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the finite packet of \autoref{def:tradition-science-registry-bridge-carrier}. Rows $T,P,R$ display the inherited tradition, the structure preserved by the comparison, and the surplus reading rejected by the BEDC site.

Rows $S,E,F$ display the science entry, its empirical ledger, and the failure surface that can block promotion. These rows specialize the registry discipline of \autoref{ch:concrete-instances-registrylayer-namecert} and the claim-export discipline of \autoref{ch:concrete-instances-claimregistrylayer-namecert} to the two registry families named in the philosophy tables.

Finally $H,C,K,N$ transport, replay, package, and name the same packet. Since the carrier contains no hidden tradition doctrine, no science promise outside the failure surface, and no empirical row outside $E$, the listed obligations exhaust the local $\NameCert_{\TraditionScienceRegistryBridgeUp}$ surface.
\end{proof}

\begin{theorem}[Tradition and science registry bridge nonescape]
\label{thm:tradition-science-registry-bridge-nonescape}
Every accepted $\TraditionScienceRegistryBridgeUp$ packet refuses a tradition export with no rejected-surplus row and refuses a science export with no failure-surface row. A consumer cannot replace $R$ or $F$ by concept-registry placement, core-index membership, registry-layer admission, claim-layer export, transport, continuation replay, package provenance, or local naming alone.
\end{theorem}
\begin{proof}
Use the obligations of \autoref{thm:tradition-science-registry-bridge-obligations}. Tradition comparison must pass through $T,P,R$, so the preserved structure and rejected surplus are displayed in the same finite packet.

Science roadmap export must pass through $S,E,F$, so empirical support and the blocking surface are displayed before the roadmap is treated as a registry export.

The sibling packets named in the statement govern concept entries, index rows, registry admission, claim export, transport, continuation, package, or naming. They preserve or route an admitted packet; they do not synthesize the missing rejected-surplus row $R$ or failure-surface row $F$. Thus any attempted export without those rows exits $\TraditionScienceRegistryBridgeUp$.
\end{proof}

\falsifiablePrediction{A tradition or science registry export that lacks either a rejected-surplus row or a failure-surface row is outside TraditionScienceRegistryBridgeUp.}

\independenceWitness{conceptregistrysurface, coreregistryindex, registrylayer, claimregistrylayer, registryexportsurface: no sibling is bijective because each controls concept, index, registry, claim, or export rows separately, while this packet binds tradition comparison and science failure-surface rows in one carrier.}

The Lean follow-up requires $\Nontrivial\ \TraditionScienceRegistryBridgeUp$ and $\FieldFaithful\ \TraditionScienceRegistryBridgeUp$ instances in \texttt{lean4/BEDC/Derived/TraditionScienceRegistryBridgeUp/TasteGate.lean}. Those instances must preserve $T,P,R,S,E,F,H,C,K,N$ as separate displayed rows before any checked theorem may cite the packet as a TasteGate surface.

\closureat{TraditionScienceRegistryBridgeUp}{seedStr}

\begin{closurestatus}{\TraditionScienceRegistryBridgeUp}
  \constructivestory{A $\TraditionScienceRegistryBridgeUp$ packet is generated from tradition-entry, preserved-structure, rejected-surplus, science-entry, empirical-ledger, failure-surface, componentwise hsame transport, displayed Cont replay, Pkg provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:tradition-science-registry-bridge-carrier}, \autoref{thm:tradition-science-registry-bridge-obligations}, and \autoref{thm:tradition-science-registry-bridge-nonescape} bind tradition comparison and science roadmap export to one finite NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, empirical correctness of science entries, or philosophical correctness of every tradition comparison.}
  \upgradepath{Lean closure requires Nontrivial TraditionScienceRegistryBridgeUp and FieldFaithful TraditionScienceRegistryBridgeUp instances in \texttt{lean4/BEDC/Derived/TraditionScienceRegistryBridgeUp/TasteGate.lean}.}
\end{closurestatus}
