\chapter{A Concrete Naming Certificate for $\RelationalPhysicsUp$}
\label{ch:concrete-instances-relational-physics-namecert}
\origin{human}

The $\RelationalPhysicsUp$ packet realizes the relational-physics site of \autoref{subsec:philosophy-relational-physics-tradition} as finite BEDC certificate data. The recognized tradition supplies the external reading that physical content is relational rather than attached to a privileged global frame; the packet below keeps the BEDC realization internal to observer-history identity, inter-history locality, inter-history invariant, physical-model audit, admissible rate or refusal rows, displayed transport, replay, provenance, and local naming.

Its sibling context is the observer-history identity surface of \autoref{ch:concrete-instances-observerhistidentity-namecert}, the invariant readback of \autoref{ch:concrete-instances-interhistinvariant-namecert}, the locality ledger of \autoref{ch:concrete-instances-inter-hist-locality-ledger-namecert}, and the physical-model audit of \autoref{ch:concrete-instances-physical-model-audit-namecert}. The philosophical horizon is the relational-physics synthesis site of \autoref{subsec:philosophy-relational-physics-tradition}.

\begin{definition}[Relational physics carrier]
\label{def:relational-physics-carrier}
A $\RelationalPhysicsUp$ carrier is a finite $\BHist$ packet
$$
R=(O,I,L,V,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the observer-history identity row, read through $\ObserverHistIdentityUp$ and carrying only history, observation, $\hsame$, $\Cont$, $\Pkg$, and local naming data.
\item $I$ is the inter-history invariant row supplied by $\InterHistInvariantUp$ after the relevant two-history packet and relation row have been displayed.
\item $L$ is the inter-history locality ledger row supplied by $\InterHistLocalityLedgerUp$, binding the two source histories, locality cells, invariant readback, and no-global-frame exclusion.
\item $V$ is the visible physical-model audit row supplied by $\PhysicalModelAuditUp$, recording source traces, observed and model signatures, classifier, tower, failure surface, and audit strength as finite packet data.
\item $A$ is the admissible rate or refusal row: it either carries a maximum-rate certificate accepted by the relevant inter-history route, or a displayed refusal that no such rate row is licensed for the packet.
\item $H$ records componentwise $\hsame$ transport for $O,I,L,V,A,C,P,N$.
\item $C$ records the displayed $\Cont$ routes by which observer identity, locality, invariant readback, model audit, admissible rate or refusal, and consumer handoff are replayed.
\item $P$ is the $\Pkg$ provenance over $\ObserverHistIdentityUp$, $\InterHistInvariantUp$, $\InterHistLocalityLedgerUp$, $\PhysicalModelAuditUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\RelationalPhysicsUp}$ row.
\end{enumerate}
The classifier compares carriers only through these rows. It has no coordinate for an absolute frame, global synchronization history, host spacetime, quotient of histories, unbounded observation stream, detached physical truth oracle, or unledgered model equivalence.
\end{definition}
\leanchecked{BEDC.Derived.RelationalPhysicsUp.RelationalPhysicsTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Relational physics NameCert obligations]
\label{thm:relational-physics-namecert-obligations}
For the carrier of \autoref{def:relational-physics-carrier}, the local $\NameCert_{\RelationalPhysicsUp}$ surface consists exactly of carrier admission for $R=(O,I,L,V,A,H,C,P,N)$, observer-history identity through $O$, inter-history locality through $L$, invariant readback through $I$, visible physical-model audit through $V$, admissible rate or displayed refusal through $A$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.RelationalPhysicsUp.RelationalPhysicsCarrier\_namecert\_obligations}
\begin{proof}
Project the accepted packet to the nine displayed rows. The rows $O,I,L,V,A$ are the only relational and physical content coordinates, while $H,C,P,N$ provide transport, replay, provenance, and naming.

Read observer identity first. The row $O$ is governed by \autoref{ch:concrete-instances-observerhistidentity-namecert}, so it supplies no observer-substance, host observer equality, or quotient identity.

Read locality and invariant content next. The row $L$ comes from the finite locality ledger of \autoref{ch:concrete-instances-inter-hist-locality-ledger-namecert}, and the row $I$ comes from the invariant readback of \autoref{ch:concrete-instances-interhistinvariant-namecert}. These rows keep the physical relation on displayed history packets rather than on a global frame.

Finally read the audit and rate boundary. The row $V$ is the visible physical-model audit of \autoref{ch:concrete-instances-physical-model-audit-namecert}, and $A$ is either the licensed rate row or the refusal row. Since the carrier contains no further physical coordinate, the listed rows exhaust the NameCert obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.RelationalPhysicsUp.RelationalPhysicsNameCertObligations}

\begin{theorem}[Relational physics invariant route exclusion]
\label{thm:relational-physics-invariant-route-exclusion}
Every accepted $\RelationalPhysicsUp$ consumer that reads relational physical content must factor through the displayed observer-history identity row $O$, locality ledger row $L$, inter-history invariant row $I$, visible physical-model audit row $V$, admissible rate or refusal row $A$, and the support rows $H,C,P,N$. No such consumer may add an absolute frame, synchronized global clock, ambient spacetime, quotient history equality, unbounded observation stream, detached physical truth oracle, or model equivalence outside the audit row.
\end{theorem}
\begin{proof}
Start with carrier admission from \autoref{def:relational-physics-carrier}. The public packet has exactly the rows $O,I,L,V,A,H,C,P,N$.

Apply the NameCert obligations of \autoref{thm:relational-physics-namecert-obligations}. They force identity, locality, invariant, audit, and rate-or-refusal reads to pass through the corresponding displayed rows before any consumer handoff can occur.

The exclusions are immediate from the carrier inventory. Absolute frames, synchronized clocks, ambient spacetime, quotient history equality, unbounded observations, detached truth oracles, and model equivalence outside the audit row are not coordinates of $R$ and cannot be created by $\hsame$, $\Cont$, $\Pkg$, or the local $\NameCert$ row.
\end{proof}
\leanchecked{BEDC.Derived.RelationalPhysicsUp.RelationalPhysicsGlobalFrameTailExclusion}

\begin{theorem}[Relational physics NameCert handoff]
\label{thm:relational-physics-namecert-handoff}
The downstream handoff from an accepted $\RelationalPhysicsUp$ packet is the finite route
$$
O,L,I,V,A,H,C,P,N.
$$
It presents relational physical content as observer-history identity, inter-history locality, invariant readback, visible model audit, admissible rate or refusal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ naming. It does not present a completed physical theory, global geometry, semantic real-valued dynamics, or bridge-checked standard model.
\end{theorem}
\leanchecked{BEDC.Derived.RelationalPhysicsUp.RelationalPhysics\_namecert\_handoff}
\begin{proof}
Project the accepted carrier and order the consumer route by the displayed dependencies. The observer-history row $O$ gives the identity surface, $L$ gives locality, $I$ gives the invariant readback, and $V$ gives the physical-model audit.

The row $A$ records whether the route carries an admissible rate certificate or an explicit refusal. Transport and replay are then supplied only by $H$ and $C$, with $P$ and $N$ recording provenance and local naming.

Apply \autoref{thm:relational-physics-invariant-route-exclusion}. The same route excludes global geometry, semantic real-valued dynamics, detached physical truth, and bridge checking because none is a displayed coordinate of the accepted packet.
\end{proof}

\falsifiablePrediction{Any accepted RelationalPhysicsUp consumer that exports relational physical content while bypassing observer-history identity, inter-history locality, invariant readback, physical-model audit, or the admissible rate and refusal row fails the carrier classifier.}

\independenceWitness{observerhistidentity, interhistinvariant, interhistlocalityledger, physicalmodelaudit: none carries observer-history identity, locality ledger, invariant readback, visible model audit, admissible rate or refusal, componentwise hsame transport, Cont replay, Pkg provenance, and one local NameCert row in a single relational-physics packet.}

\closureat{RelationalPhysicsUp}{seedStr}

\begin{closurestatus}{\RelationalPhysicsUp}
  \constructivestory{A $\RelationalPhysicsUp$ packet is generated from observer-history identity, inter-history invariant, locality ledger, physical-model audit, admissible rate or refusal, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope records the finite relational-physics carrier, its NameCert obligation surface, route exclusion, and downstream handoff.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not derive a completed physical theory, global spacetime geometry, semantic real-valued dynamics, host physical truth, or a standard bridge for relational physics.}
  \upgradepath{The next paper grade is obligation closure for the observer-history, locality, invariant, physical-model audit, rate or refusal, transport, replay, provenance, and local NameCert rows.}
\end{closurestatus}
