\chapter{A Concrete Naming Certificate for $\DyadicSplineUp$}
\label{ch:concrete-instances-dyadicspline-namecert}
\origin{human}

The $\DyadicSplineUp$ interface names finite dyadic piecewise-linear approximation data as a BEDC naming certificate. Following de Boor, \emph{A Practical Guide to Splines}, and Schumaker, \emph{Spline Functions}, the standard finite spline reading is a knot row, coefficient rows, and a segment ledger. BEDC records only those finite displayed rows and the real-name boundary through which downstream approximation consumers read them; it does not add host functions, quotient reals, choice-selected limits, or an ambient vector space of splines.

Its dependency anchors are $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, and $\DyadicApproximationUp$. The finite spline carrier consumes the dyadic mesh carrier of \autoref{ch:concrete-instances-dyadicmesh-namecert} for knot and adjacency rows, and the dyadic rational core of \autoref{ch:concrete-instances-dyadicratcore-namecert} for endpoint coefficients.

\begin{definition}[DyadicSpline finite carrier]
\label{def:dyadic-spline-finite-carrier}
A $\DyadicSplineUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
S=(K,A,L,I,Q,R,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $K$ is a $\DyadicMeshUp$ knot row, listing a finite ordered dyadic mesh and the cell adjacency data inspected by the spline reader;
\item $A$ is a finite family of $\DyadicRatCoreUp$ coefficient rows, with two endpoint coefficient reads for each retained segment;
\item $L$ is the piecewise-linear segment ledger, pairing each adjacent knot cell with its two coefficient rows and its displayed affine interpolation route;
\item $I$ is the $\RationalIntervalUp$ cell ledger through which every segment domain and endpoint order is read;
\item $Q$ is the $\RegSeqRatUp$ readback row obtained by evaluating a requested finite window against the segment ledger and coefficient rows;
\item $R$ is the $\RealUp$ seal row through which downstream real-name consumers read the same finite observation windows;
\item $H$ stores componentwise $\hsame$ transports for knots, coefficients, segment ledgers, interval cells, rational readbacks, real seals, provenance, and the local naming row;
\item $C$ stores the displayed $\Cont$ routes for mesh refinement, segment readback, interval-cell inspection, $\RegSeqRatUp$ consumption, and $\RealUp$ sealing;
\item $P$ is the $\Pkg$ provenance row naming $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\DyadicApproximationUp$, and the consumed local source certificates;
\item $N$ is the local $\NameCert_{\DyadicSplineUp}$ row.
\end{enumerate}
The classifier compares accepted carriers only after transporting them to a common displayed dyadic refinement, comparing the refined knot rows, comparing the transported coefficient rows through $\DyadicRatCoreUp$, comparing cell boundaries through $\RationalIntervalUp$, and then reading the same $\RegSeqRatUp$ and $\RealUp$ boundary rows. The carrier has no coordinate for a host function, a completed real graph, a quotient real, an infinite knot sequence, or a choice-selected limit.
\end{definition}
\leandef{BEDC.Derived.DyadicSplineUp.TasteGate.DyadicSplineUp}
\leanchecked{BEDC.Derived.DyadicSplineUp.TasteGate.DyadicSplineTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DyadicSpline NameCert obligation surface]
\label{thm:dyadic-spline-namecert-obligation-surface}
The seed $\NameCert_{\DyadicSplineUp}$ sketch has five rows:
\begin{enumerate}
\item carrier inhabitation: finite knot and coefficient packets inhabit the carrier of \autoref{def:dyadic-spline-finite-carrier};
\item classifier transport: accepted carriers are compared only after displayed transport of knots, coefficients, segment ledgers, rational cells, $\RegSeqRatUp$ readbacks, and $\RealUp$ seal rows;
\item mesh-refinement stability: displayed dyadic refinement replaces each segment by a finite family of subsegments while preserving transported endpoint coefficients and interval-cell boundaries;
\item boundary non-escape: every rational readback and real-name seal factors through the finite segment ledger, $\RationalIntervalUp$ cell row, $\RegSeqRatUp$ readback row, and $\RealUp$ seal row;
\item standard reading: the public piecewise-linear reading is exactly the finite knot row, coefficient rows, segment ledger, cell ledger, readback row, seal row, transport rows, continuation routes, package provenance, and local $\NameCert$ row.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.DyadicSplineUp.DyadicSplineFiniteCarrier\_namecert\_obligation\_surface}
\begin{proof}
Carrier inhabitation is obtained by choosing a finite $\DyadicMeshUp$ knot row and attaching two $\DyadicRatCoreUp$ coefficient reads to each adjacent knot cell. The segment ledger records the displayed affine interpolation route, and the remaining carrier coordinates are the interval, readback, seal, transport, continuation, provenance, and local name rows.

The classifier row is componentwise after common displayed refinement. Knot rows are compared through $\DyadicMeshUp$, coefficient rows through $\DyadicRatCoreUp$, cell boundaries through $\RationalIntervalUp$, and consumer-facing observations through the $\RegSeqRatUp$ and $\RealUp$ rows.

The stability, non-escape, and standard-reading rows are the three public obligations proved by the following theorems. Together they list every coordinate a downstream consumer can inspect, so the seed certificate surface is finite and contains no host function or completed real graph.
\end{proof}

\begin{theorem}[DyadicSpline mesh refinement handoff]
\label{thm:dyadic-spline-mesh-refinement-handoff}
Let $S=(K,A,L,I,Q,R,H,C,P,N)$ be an accepted $\DyadicSplineUp$ carrier. If $K'$ is obtained from $K$ by displayed $\DyadicMeshUp$ refinement and each old segment in $L$ is replaced by the finite list of subsegments induced by the refined knot row, with endpoint coefficient rows transported through the same $\hsame$ witnesses, then the refined packet
$$
S'=(K',A',L',I',Q',R',H',C',P,N)
$$
is again an accepted $\DyadicSplineUp$ carrier. Its $\RegSeqRatUp$ and $\RealUp$ consumer rows factor through the same finite piecewise-linear reading, now displayed on the refined mesh.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicSplineUp.DyadicSplinePacket\_mesh\_refinement\_handoff}
\begin{proof}
Project the carrier of \autoref{def:dyadic-spline-finite-carrier}. The knot row, coefficient rows, and segment ledger are finite, so a displayed mesh refinement subdivides each old segment into a finite family of adjacent subsegments.

Transport the endpoint coefficient rows along $H$. The refined segment ledger $L'$ uses the transported endpoint rows and the same affine readback route restricted to each refined cell, while $I'$ records the corresponding $\RationalIntervalUp$ cell boundaries.

Route the rational readback row $Q'$ and real seal row $R'$ through the refined continuation routes in $C'$. Repacking these rows gives exactly the carrier coordinates, so the refined packet is accepted and exposes the same piecewise-linear data on the finer displayed mesh.
\end{proof}

\begin{theorem}[DyadicSpline endpoint mesh transport stability]
\label{thm:dyadic-spline-endpoint-mesh-transport-stability}
Let $S=(K,A,L,I,Q,R,H,C,P,N)$ be an accepted $\DyadicSplineUp$ packet, and let $K'$ be a displayed refinement of the mesh row $K$. When the endpoint coefficient rows in $A$, the rational cell rows in $I$, and the segment ledger rows in $L$ are transported componentwise along the displayed $\hsame$ witnesses in $H$, the refined rows assemble with the transported $\RegSeqRatUp$ readbacks and $\RealUp$ seals into one classifier-facing packet
$$
S'=(K',A',L',I',Q',R',H',C',P,N).
$$
The accepted comparison between $S$ and $S'$ is exhausted by the displayed knot, endpoint, cell, ledger, readback, and seal transports together with the $\Cont$ routes for refined-cell inspection. No host function, graph, quotient real, infinite knot sequence, or selected limit is introduced by the handoff.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-spline-finite-carrier}. The knot row, endpoint coefficient family, segment ledger, rational cell ledger, readback row, seal row, transport row, continuation row, provenance row, and local name row are all explicit coordinates of $S$.

Use the displayed $\hsame$ entries in $H$ to move the knot row to $K'$ and to move each endpoint coefficient row to the refined endpoint ledger. The rational cell rows move by the same componentwise transport, and each refined segment in $L'$ records the transported endpoints and the corresponding cell row.

Route every refined rational observation through the displayed $\Cont$ entries in $C$. The $\RegSeqRatUp$ readback row $Q'$ and $\RealUp$ seal row $R'$ are therefore read only after the refined segment and rational cell rows have been selected.

Repacking these transported coordinates gives the packet $S'$ named in the statement. Since every inspected coordinate is a carrier projection or a displayed continuation route, there is no remaining place for a host function, graph, quotient real, infinite knot sequence, or selected limit to enter the classifier.
\end{proof}

\begin{theorem}[DyadicSpline RegSeqRat Real boundary]
\label{thm:dyadic-spline-regseqrat-real-boundary}
For every accepted $\DyadicSplineUp$ carrier $S=(K,A,L,I,Q,R,H,C,P,N)$ and every finite consumer window, the $\RegSeqRatUp$ readback and $\RealUp$ seal are reached only by first selecting a displayed segment from $L$, reading its $\RationalIntervalUp$ cell from $I$, reading its endpoint coefficients from $A$, and routing the resulting finite rational observation through $Q$ and $R$.

The boundary exports finite rational observations and real-name seal rows only. It does not export quotient stream equality, an ambient real-valued function, a host graph, uniform convergence of a sequence of splines, or a choice-selected limit.
\end{theorem}
\leanchecked{BEDC.Derived.DyadicSplineUp.DyadicSplinePacket\_regseqrat\_real\_boundary}
\begin{proof}
Start with the requested finite window. The carrier selects a segment through the knot row $K$ and the segment ledger $L$; no other coordinate can choose a domain cell.

Read the selected cell through $I$ and the two endpoint coefficient rows through $A$. The displayed affine interpolation route in $L$ turns these finite dyadic rows into a rational observation at the requested window.

The observation is then routed through the $\RegSeqRatUp$ row $Q$ and sealed through the $\RealUp$ row $R$. Since every step is a projection from the finite carrier and its displayed continuation routes, quotient stream equality, host functions, graphs, uniform convergence, and choice-selected limits remain outside the exported boundary.
\end{proof}

\begin{theorem}[DyadicSpline standard piecewise-linear reading]
\label{thm:dyadic-spline-standard-piecewise-linear-reading}
The standard finite piecewise-linear reading of an accepted $\DyadicSplineUp$ carrier is exactly the tuple consisting of the $\DyadicMeshUp$ knot row, finite $\DyadicRatCoreUp$ coefficient rows, segment ledger, $\RationalIntervalUp$ cell ledger, $\RegSeqRatUp$ readback row, $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ row.

This reading is stable under the mesh-refinement handoff of \autoref{thm:dyadic-spline-mesh-refinement-handoff} and has the non-escape boundary of \autoref{thm:dyadic-spline-regseqrat-real-boundary}. It is the whole public surface exported to $\DyadicApproximationUp$ consumers.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:dyadic-spline-finite-carrier}. Its rows are precisely the knot row, coefficient rows, segment ledger, cell ledger, rational readback, real seal, transport, continuation, provenance, and local name coordinates.

Apply \autoref{thm:dyadic-spline-mesh-refinement-handoff}. Refinement changes the displayed mesh and segment ledger by finite subdivision, while preserving the transported endpoint coefficients and consumer-facing readback route.

Apply \autoref{thm:dyadic-spline-regseqrat-real-boundary}. The $\RegSeqRatUp$ and $\RealUp$ boundary rows are reached only through the finite segment and cell ledgers, so no extra analytic object can be exported.

The downstream $\DyadicApproximationUp$ consumer therefore receives exactly the finite piecewise-linear tuple named in the statement. There is no remaining carrier coordinate from which a host function, completed real graph, quotient real, or choice-selected limit could be read.
\end{proof}

\begin{theorem}[DyadicApproximation DyadicSpline consumer route]
\label{thm:dyadic-approximation-dyadic-spline-consumer-route}
Every $\DyadicApproximationUp$ consumer of an accepted $\DyadicSplineUp$ packet must read the packet through the $\DyadicApproximationUp$ chapter surface of \autoref{ch:concrete-instances-dyadicapproximation-namecert} together with the displayed $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, and $\RealUp$ rows of \autoref{def:dyadic-spline-finite-carrier}.

The consumer route is exactly the finite piecewise-linear tuple of \autoref{thm:dyadic-spline-standard-piecewise-linear-reading}, transported through the mesh-refinement handoff of \autoref{thm:dyadic-spline-mesh-refinement-handoff} and sealed by the $\RegSeqRatUp$/$\RealUp$ boundary of \autoref{thm:dyadic-spline-regseqrat-real-boundary}. It exports no host spline function, quotient real graph, selected limit, ambient completion, infinite knot row, or independent analytic approximation object.
\end{theorem}
\begin{proof}
Start with an accepted packet $S=(K,A,L,I,Q,R,H,C,P,N)$. The standard reading theorem identifies the public surface of $S$ with the displayed mesh row, endpoint coefficient rows, segment ledger, rational cell ledger, readback row, seal row, transports, continuations, provenance, and local name row.

A $\DyadicApproximationUp$ consumer reaches that surface through \autoref{ch:concrete-instances-dyadicapproximation-namecert}. Its dyadic observations therefore read the $\DyadicRatCoreUp$ coefficients along the $\DyadicMeshUp$ cells, inspect the $\RationalIntervalUp$ cell ledger, and pass the resulting finite observation through the $\RegSeqRatUp$ and $\RealUp$ rows.

If the consumer asks for a finer displayed window, apply the mesh-refinement handoff. Refinement replaces the mesh and segment ledger by finite subdivided rows while keeping the transported endpoint coefficients, rational cell boundaries, and consumer-facing readback route inside the same carrier format.

Finally apply the RegSeqRat/Real boundary theorem. Since the route to the seal factors through the finite segment and cell ledgers before reaching $Q$ and $R$, there is no coordinate from which the consumer can read a host function, quotient real graph, selected limit, ambient completion, infinite knot row, or separate analytic approximation object.
\end{proof}

\begin{theorem}[DyadicSpline common refinement segment exhaustion]
\label{thm:dyadic-spline-common-refinement-segment-exhaustion}
Let $S=(K,A,L,I,Q,R,H,C,P,N)$ and $S'=(K',A',L',I',Q',R',H',C',P',N')$ be accepted $\DyadicSplineUp$ packets compared by classifier transport. Then their comparison refines to one displayed dyadic mesh and one finite segment ledger. Every compared endpoint coefficient, rational cell, $\RegSeqRatUp$ readback, and $\RealUp$ seal read factors through that common mesh and ledger.

The exhaustion exports only the shared $\DyadicMeshUp$ row, finite $\DyadicRatCoreUp$ endpoint coefficients, $\RationalIntervalUp$ cell rows, segment ledger, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. It does not read a host function, completed graph, quotient real, infinite knot sequence, or selected limit.
\end{theorem}
\begin{proof}
Project both accepted packets through \autoref{def:dyadic-spline-finite-carrier}. The classifier compares knot rows, endpoint coefficient rows, rational cell rows, segment ledgers, readback rows, seal rows, and provenance rows only after displayed transport.

Apply \autoref{thm:dyadic-spline-mesh-refinement-handoff} to refine both mesh rows to a common displayed dyadic mesh. Then apply \autoref{thm:dyadic-spline-endpoint-mesh-transport-stability} to transport the endpoint coefficients, interval cells, and segment ledgers onto that common mesh.

Finally use \autoref{thm:dyadic-spline-standard-piecewise-linear-reading}. Once the packets have been transported to the same mesh, the public read is exactly the finite mesh, endpoint, cell, ledger, readback, seal, transport, continuation, provenance, and local naming tuple, so no host-level reading remains.
\end{proof}

\begin{theorem}[DyadicSpline zero segment carrier]
\label{thm:dyadic-spline-zero-segment-carrier}
The constant zero endpoint coefficient packet inhabits the $\DyadicSplineUp$ carrier. Its segment ledger has the displayed zero $\DyadicRatCoreUp$ endpoint rows on every retained cell, its $\RegSeqRatUp$ readback is the zero readback route, and its $\RealUp$ seal factors through that same zero readback.

This carrier is a finite BEDC packet over $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ only. It does not add a host zero function, completed graph, quotient real, infinite mesh, or selected limit.
\end{theorem}
\begin{proof}
Start with any displayed finite $\DyadicMeshUp$ row and choose the zero $\DyadicRatCoreUp$ coefficient row at both endpoints of each retained segment. The definition of \autoref{def:dyadic-spline-finite-carrier} then supplies the finite segment ledger, the rational cell ledger, transport rows, continuation rows, provenance, and local name row.

Read a consumer window through the segment ledger. Because both endpoint coefficient rows on every segment are the displayed zero rows, the resulting finite rational observation is the zero $\RegSeqRatUp$ readback.

Apply \autoref{thm:dyadic-spline-regseqrat-real-boundary} to route the $\RealUp$ seal through that readback, and apply \autoref{thm:dyadic-spline-standard-piecewise-linear-reading} to identify the public packet with the finite zero mesh data. No separate host zero function or completed graph is introduced.
\end{proof}

\begin{theorem}[DyadicSpline Real seal mesh factorization]
\label{thm:dyadic-spline-real-seal-mesh-factorization}
Every $\RealUp$ seal consumer read of an accepted $\DyadicSplineUp$ packet factors through the displayed mesh, cell ledger, endpoint coefficients, $\RegSeqRatUp$ readback, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. The consumer reaches the seal only after selecting a finite mesh cell, reading its endpoint coefficients, and passing the resulting rational observation through the regular-rational readback.

The factorization exports no host function semantics, completed real graph, quotient real, uniform convergence claim, infinite knot sequence, or choice-selected limit.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:dyadic-spline-finite-carrier}. The only seal-facing coordinates are the mesh row, endpoint coefficient rows, segment ledger, rational cell ledger, readback row, real seal row, transports, continuations, provenance, and local naming row.

Apply \autoref{thm:dyadic-spline-regseqrat-real-boundary}. A real-name consumer first chooses a displayed segment, reads its $\RationalIntervalUp$ cell and endpoint coefficients, and then routes the finite rational observation through the $\RegSeqRatUp$ row before the $\RealUp$ seal is consumed.

Apply \autoref{thm:dyadic-spline-common-refinement-segment-exhaustion} when the consumer compares transported packets, and apply \autoref{thm:dyadic-spline-standard-piecewise-linear-reading} to identify the exported surface. Thus every seal read factors through the finite mesh package, with no ambient analytic object available to the consumer.
\end{proof}

\begin{theorem}[DyadicSpline refinement classifier transport]
\label{thm:dyadic-spline-refinement-classifier-transport}
Let $S=(K,A,L,I,Q,R,H,C,P,N)$ and $S'=(K',A',L',I',Q',R',H',C',P',N')$ be accepted $\DyadicSplineUp$ packets whose classifier comparison is displayed on a common dyadic refinement. Then the classifier transports the knot rows, endpoint coefficient rows, segment ledgers, rational cell rows, $\RegSeqRatUp$ readbacks, and $\RealUp$ seal rows through that same refinement.

The transported comparison is exhausted by the $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates of the two finite carriers. It has no coordinate for a host spline function, completed graph, quotient real, infinite knot sequence, or selected limit.
\end{theorem}
\begin{proof}
Project both packets through \autoref{def:dyadic-spline-finite-carrier}. The only classifier-facing rows are the displayed knot, endpoint, segment, cell, readback, seal, transport, continuation, provenance, and local naming coordinates.

Apply \autoref{thm:dyadic-spline-common-refinement-segment-exhaustion}. The comparison first moves both carriers to one displayed dyadic mesh and one finite segment ledger, so every later read is made on that common finite row.

Apply \autoref{thm:dyadic-spline-endpoint-mesh-transport-stability}. Endpoint coefficients, cell rows, segment entries, rational readbacks, and real seals move componentwise along the stored $\hsame$ witnesses and displayed $\Cont$ routes.

The standard reading theorem then identifies the transported packet with the same finite piecewise-linear surface. Since each inspected item is a carrier projection or displayed continuation route, no host-level analytic object remains in the classifier.
\end{proof}

\begin{theorem}[DyadicSpline Real seal stability]
\label{thm:dyadic-spline-real-seal-stability}
For every accepted $\DyadicSplineUp$ packet and every displayed dyadic refinement accepted by \autoref{thm:dyadic-spline-mesh-refinement-handoff}, each $\RealUp$ seal read after refinement is still routed through a selected segment row, its rational cell row, its transported endpoint coefficient rows, and the $\RegSeqRatUp$ readback row.

Thus refinement preserves the real-seal non-escape boundary: the seal read remains inside the finite $\DyadicMeshUp$, $\DyadicRatCoreUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ packet.
\end{theorem}
\begin{proof}
Start with the refined packet supplied by \autoref{thm:dyadic-spline-mesh-refinement-handoff}. Its refined mesh, endpoint rows, segment ledger, cell ledger, readback row, seal row, transports, continuations, provenance, and local name are again the coordinates of \autoref{def:dyadic-spline-finite-carrier}.

Use \autoref{thm:dyadic-spline-real-seal-mesh-factorization}. A seal consumer first selects a finite mesh cell, reads its transported endpoint coefficients, and then reaches the $\RegSeqRatUp$ row before the $\RealUp$ seal is consumed.

The boundary theorem \autoref{thm:dyadic-spline-regseqrat-real-boundary} excludes every route outside those finite rows. Therefore mesh refinement changes the displayed carrier rows but does not open a path to host functions, quotient reals, completed graphs, infinite meshes, or selected limits.
\end{proof}

\begin{theorem}[DyadicSpline obligation closure package]
\label{thm:dyadic-spline-obligation-closure-package}
The finite carrier of \autoref{def:dyadic-spline-finite-carrier}, the NameCert obligation surface of \autoref{thm:dyadic-spline-namecert-obligation-surface}, the mesh-refinement handoff, the endpoint transport stability theorem, the rational-real boundary theorem, the standard piecewise-linear reading, the refinement classifier transport theorem, and the real-seal stability theorem assemble the $\DyadicSplineUp$ obligation package.

The package supplies carrier habitation, classifier transport, mesh-refinement stability, readback boundary, real-seal stability, and the standard finite piecewise-linear reading for $\DyadicSplineUp$ consumers. It asserts no host-function semantics, quotient real, completed spline graph, infinite knot sequence, uniform convergence theorem, or choice-selected limit.
\end{theorem}
\begin{proof}
Carrier habitation and the row inventory are supplied by \autoref{def:dyadic-spline-finite-carrier} and \autoref{thm:dyadic-spline-namecert-obligation-surface}. They expose the finite mesh, endpoint, segment, cell, readback, seal, transport, continuation, package, and local name rows.

Mesh-refinement stability is \autoref{thm:dyadic-spline-mesh-refinement-handoff}, with endpoint and cell transport supplied by \autoref{thm:dyadic-spline-endpoint-mesh-transport-stability}. The classifier transport theorem places the compared packets on the same displayed refinement before any consumer read.

The readback and seal boundaries are supplied by \autoref{thm:dyadic-spline-regseqrat-real-boundary} and \autoref{thm:dyadic-spline-real-seal-stability}. Finally, \autoref{thm:dyadic-spline-standard-piecewise-linear-reading} identifies the public reading with exactly those rows, so the assembled obligation package has no remaining analytic escape coordinate.
\end{proof}

\closureat{DyadicSplineUp}{seedStr}
\closureat{DyadicSplineUp}{obligationStr}[BEDC.Derived.DyadicSplineUp.DyadicSplineFiniteCarrier\_namecert\_obligation\_surface]
\closureat{DyadicSplineUp}{scopedStr}[BEDC.Derived.DyadicSplineUp.DyadicSplineFiniteCarrier\_namecert\_obligation\_surface]
\closureat{DyadicSplineUp}{publicStr}[BEDC.Derived.DyadicSplineUp.DyadicSplineFiniteCarrier\_namecert\_obligation\_surface]

\begin{closurestatus}{\DyadicSplineUp}
  \constructivestory{A $\DyadicSplineUp$ packet is generated by a finite $\DyadicMeshUp$ knot row, finite $\DyadicRatCoreUp$ coefficient rows, a piecewise-linear segment ledger, a $\RationalIntervalUp$ cell ledger, a $\RegSeqRatUp$ readback row, a $\RealUp$ seal row, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{\autoref{thm:dyadic-spline-standard-piecewise-linear-reading} and \autoref{thm:dyadic-spline-obligation-closure-package} export the public finite piecewise-linear reading and obligation package over $\DyadicRatCoreUp$, $\DyadicMeshUp$, $\RationalIntervalUp$, $\RegSeqRatUp$, $\RealUp$, and $\DyadicApproximationUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.DyadicSplineUp.DyadicSplineFiniteCarrier\_namecert\_obligation\_surface}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host-function semantics, quotient reals, infinite knot sequences, uniform convergence of spline families, choice-selected limits, or bridge checking.}
  \upgradepath{Bridge closure requires bridge evidence beyond the public finite packet and its standard piecewise-linear reading.}
\end{closurestatus}
