\chapter{A Concrete Naming Certificate for $\CauchyLimitSealUp$}
\label{ch:concrete-instances-cauchylimitseal-namecert}
\origin{human}

The $\CauchyLimitSealUp$ interface records the visible seal boundary between regular rational Cauchy data and the consumer-facing $\RealUp$ row. In the Bishop--Bridges constructive-analysis reading of Cauchy completion, a limit is presented by finite regular-name observations and an explicit schedule, not by quotienting streams or selecting a host limit. The chapter isolates that boundary as a concrete packet so later $\RealUp$ consumers can read only the displayed finite windows that pass through the seal.

\begin{definition}[CauchyLimitSeal carrier]
\label{def:cauchy-limit-seal-carrier}
A $\CauchyLimitSealUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
L=(X,S,D,G,E,T,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $X$ is a $\RegSeqRatUp$ family row presenting the regular rational Cauchy source to be sealed;
\item $S$ is the $\StreamNameUp$ schedule that lists the finite windows a consumer may inspect;
\item $D$ is the $\DyadicRatCore$ observation ledger attached to those scheduled windows;
\item $G$ is the $\RealCauchyCompletionUp$ diagonal row that routes the regular family through its displayed completion packet;
\item $E$ is the $\RealUp$ seal row exposed to downstream real consumers;
\item $T$ is the finite collection of $\hsame$ and $\Cont$ transport rows connecting the source family, scheduled windows, diagonal row, observation ledger, and seal row;
\item $P$ is the $\Pkg$ provenance row naming the $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, and $\RealUp$ dependency certificates;
\item $N$ is the local $\NameCert_{\CauchyLimitSealUp}$ row.
\end{enumerate}
The local classifier compares two carriers only by componentwise transport of these visible rows. It does not compare quotient representatives, host limits, or ambient completeness data.
\end{definition}

\begin{theorem}[CauchyLimitSeal NameCert obligations]
\label{thm:cauchy-limit-seal-namecert-obligations}
The $\NameCert_{\CauchyLimitSealUp}$ surface has four finite obligations: carrier habitation by \autoref{def:cauchy-limit-seal-carrier}; classifier stability under the displayed $\hsame$ and $\Cont$ transport rows; exact factorization of every $\RealUp$ consumer read through the $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCore$, and $\RealCauchyCompletionUp$ rows; and non-escape of quotient stream equality, selected host limits, uniqueness theorems, and ambient real completeness data.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_namecert\_obligations}
\begin{proof}
Carrier habitation is the finite packet assembly. The regular family, schedule, observation ledger, completion row, seal row, transport rows, package provenance, and local certificate are all coordinates of the displayed $\mathsf{BHist}$ packet.

Classifier stability is componentwise. Each row is transported only by the stored $\hsame$ comparison and the corresponding $\Cont$ route, so an accepted packet stays inside the same visible dependency surface.

The exactness and boundary obligations follow from the shape of the carrier. Every $\RealUp$ read must pass through the scheduled finite windows and their dyadic observation ledger before reaching the completion row and seal row; no field contains a quotient stream, a selected host limit, a uniqueness theorem, or an ambient real-completeness datum.
\end{proof}

\begin{theorem}[CauchyLimitSeal window factorization]
\label{thm:cauchy-limit-seal-window-factorization}
For every accepted $\CauchyLimitSealUp$ carrier $L$ and every finite $\RealUp$ consumer request, the read factors through a visible $\StreamNameUp$ window from $S$, the corresponding $\RegSeqRatUp$ source row in $X$, the matching $\DyadicRatCore$ observation ledger in $D$, the $\RealCauchyCompletionUp$ diagonal row $G$, and the displayed transport rows in $T$ before it reaches the seal row $E$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealPacket\_window\_factorization}
\begin{proof}
Project the carrier of \autoref{def:cauchy-limit-seal-carrier}. A consumer request first selects one of the scheduled finite windows because the seal row has no independent read channel.

Read the selected window through the $\RegSeqRatUp$ source family. The rational observation is recorded in the $\DyadicRatCore$ ledger, and the same scheduled row is passed to the $\RealCauchyCompletionUp$ diagonal coordinate.

Finally apply the stored $\hsame$ and $\Cont$ rows in $T$ to transport the read to the $\RealUp$ seal. The path is therefore the stated finite factorization, with every consumer-facing value mediated by visible packet data.
\end{proof}

\begin{theorem}[CauchyLimitSeal non-escape boundary]
\label{thm:cauchy-limit-seal-non-escape}
An accepted $\CauchyLimitSealUp$ carrier exports no quotient stream, no selected host limit, no uniqueness theorem for limits, and no ambient real completeness datum. Its public surface is exhausted by the finite $\mathsf{BHist}$ packet, the $\RegSeqRatUp$ source family, the $\StreamNameUp$ schedule, the $\DyadicRatCore$ observation ledger, the $\RealCauchyCompletionUp$ diagonal row, the $\RealUp$ seal row, and the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ provenance.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates. Each coordinate is either a named dependency certificate row, a finite transport row, a package provenance row, or the local certificate row.

The completion coordinate is consumed only through its displayed diagonal row, and the real-facing coordinate is the seal row attached to that diagonal route. Neither coordinate adds a host real carrier or a quotient of regular streams.

Thus a downstream consumer can cite exactly the listed rows. Since no other coordinate exists in the packet, uniqueness theorems, selected limits, and ambient real completeness data cannot be exported by the $\CauchyLimitSealUp$ surface.
\end{proof}

\begin{theorem}[CauchyLimitSeal RealUp consumer boundary]
\label{thm:cauchy-limit-seal-realup-consumer-boundary}
Every $\RealUp$ consumer of an accepted $\CauchyLimitSealUp$ carrier may read only the sealed finite-window route of \autoref{thm:cauchy-limit-seal-window-factorization}. In particular, the consumer boundary is the displayed packet surface over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCore$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, and it does not expose an independent completeness theorem for $\RealUp$.
\end{theorem}
\leanchecked{BEDC.Derived.CauchyLimitSealUp.CauchyLimitSealCarrier\_realup\_consumer\_boundary}
\begin{proof}
Begin with the factorization theorem. It forces each consumer read through the scheduled window, regular rational source row, dyadic observation ledger, completion diagonal row, and transport route before the read reaches the $\RealUp$ seal.

Use the non-escape boundary to identify what remains visible after the seal is reached. The package provenance and local certificate name the dependency rows, but they do not add quotient, host-limit, uniqueness, or ambient-completeness fields.

Therefore the $\RealUp$ consumer boundary is precisely the finite route listed in the statement. The seal is a public endpoint for displayed regular-Cauchy data, not a source of an independent real-completeness principle.
\end{proof}

\begin{definition}[CauchyLimitSeal public route packet]
\label{def:cauchy-limit-seal-public-route-packet}
For an accepted $\CauchyLimitSealUp$ carrier $L=(X,S,D,G,E,T,P,N)$, its public route packet is the componentwise projection
$$
\mathsf{PubRoute}(L)=(X,S,D,G,E,T,P,N)
$$
read as the visible $\RegSeqRatUp$ source row, scheduled $\StreamNameUp$ window family, $\DyadicRatCoreUp$ observation ledger, $\RealCauchyCompletionUp$ diagonal row, $\RealUp$ seal row, displayed $\hsame$ and $\Cont$ transport ledger, $\Pkg$ provenance row, and local $\NameCert$ row. The packet is a named public BEDC object: it contains only these carrier coordinates and no quotient stream, selected host limit, uniqueness theorem, host real construction, or ambient completeness datum.
\end{definition}

\begin{theorem}[CauchyLimitSeal public route transport]
\label{thm:cauchy-limit-seal-public-route-transport}
Local classifier transport of accepted $\CauchyLimitSealUp$ carriers transports the public route packet componentwise. The transported packet preserves the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, and it introduces no quotient stream, selected host limit, uniqueness theorem, or ambient completeness datum.
\end{theorem}
\begin{proof}
Project the carrier $L=(X,S,D,G,E,T,P,N)$ and read \autoref{def:cauchy-limit-seal-public-route-packet}. The public route packet is exactly the visible coordinate list of the carrier, so classifier transport can act only on those coordinates.

Apply the carrier obligation theorem \autoref{thm:cauchy-limit-seal-namecert-obligations}. Its classifier-stability clause moves accepted carriers along the stored $\hsame$ comparisons and $\Cont$ routes, while the $\Pkg$ and $\NameCert$ rows keep the dependency names fixed.

Use the non-escape boundary \autoref{thm:cauchy-limit-seal-non-escape}. Because the carrier contains no quotient stream, selected host limit, uniqueness theorem, or ambient completeness field, componentwise transport cannot create any such public coordinate.
\end{proof}

\begin{theorem}[CauchyLimitSeal public route boundary]
\label{thm:cauchy-limit-seal-public-route-boundary}
Every public $\RealUp$ or completion-consumer route of an accepted $\CauchyLimitSealUp$ carrier factors through the public route packet of \autoref{def:cauchy-limit-seal-public-route-packet}. Conversely, every row of that packet is one of the displayed rows named by the finite-window factorization of \autoref{thm:cauchy-limit-seal-window-factorization} and the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}.
\end{theorem}
\begin{proof}
For a $\RealUp$ consumer, apply \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}. The read is forced through the displayed $\RegSeqRatUp$ source, scheduled $\StreamNameUp$ window, $\DyadicRatCoreUp$ observation ledger, $\RealCauchyCompletionUp$ diagonal row, $\RealUp$ seal row, and visible transport, package, and naming rows.

For a completion-facing consumer, use the finite-window factorization \autoref{thm:cauchy-limit-seal-window-factorization}. It gives the same route before the read reaches the seal, so the completion-facing path also lands inside the packet coordinates $X,S,D,G,E,T,P,N$.

The reverse containment is just projection from \autoref{def:cauchy-limit-seal-public-route-packet}. Each packet row is one of the displayed carrier rows named by the two boundary theorems, and \autoref{thm:cauchy-limit-seal-non-escape} rules out any additional public row outside that list.
\end{proof}

\begin{theorem}[CauchyLimitSeal obligation closure package]
\label{thm:cauchy-limit-seal-obligation-closure-package}
The carrier definition, the $\NameCert_{\CauchyLimitSealUp}$ obligations, the finite-window factorization, the non-escape boundary, and the $\RealUp$ consumer boundary jointly supply the full paper-side obligation surface for $\CauchyLimitSealUp$ over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCore$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The package preserves the exclusions on quotient streams, selected host limits, uniqueness of limits, host real construction, and ambient completeness.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:cauchy-limit-seal-carrier}. Its coordinates name exactly the regular rational source, schedule, dyadic ledger, completion row, real seal, transport rows, package provenance, and local certificate that form the public packet.

Apply the component obligations in order. The $\NameCert$ obligation theorem supplies habitation, classifier stability, exactness, and non-escape requirements; the window factorization theorem identifies the consumer route through the scheduled finite observations; the non-escape theorem records the absent quotient, host-limit, uniqueness, and completeness fields; and the $\RealUp$ consumer-boundary theorem fixes the public endpoint of the route.

These rows are finite and exhaust the displayed packet surface. Since the carrier contains no further coordinate from which an omitted quotient, selected limit, uniqueness principle, host real, or ambient-completeness datum could be read, the listed component rows provide the whole paper-side obligation package.
\end{proof}

\begin{theorem}[CauchyLimitSeal public export certificate]
\label{thm:cauchy-limit-seal-public-export-certificate}
The carrier, $\NameCert$ obligations, finite-window factorization, non-escape boundary, $\RealUp$ consumer boundary, and obligation closure package assemble a public certificate for the sealed finite-window route over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$. The exported certificate exposes exactly the displayed source row, scheduled window, dyadic observation ledger, diagonal completion row, seal row, transport rows, package provenance, and local certificate.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:cauchy-limit-seal-carrier}. It supplies the displayed regular source, schedule, dyadic ledger, diagonal completion row, real seal, transport rows, package provenance, and local certificate.

Apply the $\NameCert$ obligations of \autoref{thm:cauchy-limit-seal-namecert-obligations}. They provide carrier habitation, classifier stability, exactness of the consumer route, and the non-escape clauses needed for a public certificate.

Next use the window factorization theorem \autoref{thm:cauchy-limit-seal-window-factorization} and the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}. These identify the public read route through the scheduled finite window, dyadic observation ledger, completion diagonal, and seal row.

Finally combine the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape} with the obligation closure package of \autoref{thm:cauchy-limit-seal-obligation-closure-package}. The rows listed there exhaust the public surface, so the assembled certificate exports the sealed finite-window route and nothing outside the stated BEDC coordinates.
\end{proof}

\begin{theorem}[CauchyLimitSeal downstream completion handoff]
\label{thm:cauchy-limit-seal-downstream-completion-handoff}
A downstream completion consumer of an accepted $\CauchyLimitSealUp$ carrier can pull back only along the displayed $\RegSeqRatUp$ source, scheduled $\StreamNameUp$ window, $\DyadicRatCoreUp$ observation ledger, $\RealCauchyCompletionUp$ diagonal row, and $\RealUp$ seal. The handoff carries the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows and does not export an independent completeness principle, quotient stream, selected host limit, uniqueness theorem, or host real construction.
\end{theorem}
\begin{proof}
Apply the window factorization theorem \autoref{thm:cauchy-limit-seal-window-factorization}. It forces every downstream read through the scheduled $\StreamNameUp$ window, the displayed $\RegSeqRatUp$ source row, the corresponding dyadic observation ledger, and the $\RealCauchyCompletionUp$ diagonal row before reaching the $\RealUp$ seal.

Use the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape}. The accepted carrier has no field for quotient streams, selected host limits, uniqueness theorems, host real construction, or ambient completeness.

The public export certificate of \autoref{thm:cauchy-limit-seal-public-export-certificate} packages the remaining rows as the consumer-facing handoff. Thus a completion consumer can pull back only through the displayed finite-window route and its visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.
\end{proof}

\begin{theorem}[CauchyLimitSeal null-sequence factorization]
\label{thm:cauchy-limit-seal-nullsequence-factorization}
Let two sealed $\RealUp$ reads be presented by accepted $\CauchyLimitSealUp$ carriers. If their displayed difference is accepted by a $\NullSequenceUp$ packet, then every equality-consumer route factors through the CauchyLimitSeal scheduled $\StreamNameUp$ window, the $\DyadicRatCoreUp$ observation ledger, the $\RealCauchyCompletionUp$ diagonal row, the $\RealUp$ seal row, and the $\NullSequenceUp$ tolerance-window-threshold packet. The factored route carries only the visible $\RegSeqRatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows supplied by those packets, and it exports no ambient real completeness, quotient stream equality, selected host limit, or hidden tail witness.
\end{theorem}
\begin{proof}
Begin with the local window factorization theorem \autoref{thm:cauchy-limit-seal-window-factorization}. It sends each sealed read through the scheduled finite window, the dyadic observation ledger, and the completion diagonal row before any $\RealUp$ seal coordinate is consumed.

Apply the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}. This confines the equality-facing read to the displayed seal row and the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.

Next use the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff}. A completion consumer may pull back only along the same scheduled window, observation ledger, diagonal row, and seal route, so the comparison cannot introduce a second completion object.

Finally attach the $\NullSequenceUp$ real-seal factorization of \autoref{thm:null-sequence-real-seal-factorization}. Its tolerance row, observation window, and threshold row supply the zero-tail evidence read by the two seals, and the combined route remains the finite CauchyLimitSeal route plus that displayed null-sequence packet.
\end{proof}

\begin{theorem}[CauchyLimitSeal regular-source stability]
\label{thm:cauchy-limit-seal-regular-source-stability}
Let $L$ be an accepted $\CauchyLimitSealUp$ carrier. Any classifier transport of the accepted seal preserves the displayed $\RegSeqRatUp$ source row, the scheduled $\StreamNameUp$ windows, the $\DyadicRatCoreUp$ observation ledger, the $\RealCauchyCompletionUp$ diagonal row, and the $\RealUp$ seal row through the stored $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of $L$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:cauchy-limit-seal-carrier}. The source row, schedule, dyadic ledger, diagonal row, seal row, transport rows, package row, and local certificate are named coordinates of the same finite $\mathsf{BHist}$ packet.

Apply the classifier-stability clause of \autoref{thm:cauchy-limit-seal-namecert-obligations}. Transport can move an accepted packet only along the displayed $\hsame$ comparison and the corresponding $\Cont$ route, while the $\Pkg$ and $\NameCert$ rows keep the dependency names fixed.

Finally use the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape}. Since no quotient stream, selected host limit, uniqueness theorem, or ambient completeness coordinate is available, the transported seal still exposes exactly the displayed regular source, scheduled windows, observation ledger, diagonal row, and seal row.
\end{proof}

\begin{theorem}[CauchyLimitSeal diagonal-row compatibility]
\label{thm:cauchy-limit-seal-diagonal-row-compatibility}
Every $\RealCauchyCompletionUp$ diagonal read consumed by an accepted $\CauchyLimitSealUp$ seal factors through the same scheduled $\StreamNameUp$ window and the same $\DyadicRatCoreUp$ observation ledger as the finite route of \autoref{thm:cauchy-limit-seal-window-factorization}. Consequently the diagonal row $G$ in the carrier cannot be replaced, for that seal read, by an independent completion object outside the displayed packet.
\end{theorem}
\begin{proof}
Begin with the window factorization theorem \autoref{thm:cauchy-limit-seal-window-factorization}. It sends each consumer read through a scheduled $\StreamNameUp$ window, the displayed $\RegSeqRatUp$ source row, the matching $\DyadicRatCore$ ledger, and then the $\RealCauchyCompletionUp$ diagonal coordinate before the read reaches the $\RealUp$ seal.

Use the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff}. A completion consumer may pull back only along that displayed route, so the diagonal read is tied to the same scheduled window and observation ledger that feed the seal.

The carrier has no second completion coordinate. By \autoref{thm:cauchy-limit-seal-non-escape}, no host limit, quotient stream, or ambient completeness datum can supply an alternate completion object; therefore the diagonal row consumed by the seal is the carrier row $G$ routed through the stated finite ledger.
\end{proof}

\begin{theorem}[CauchyLimitSeal seal-ledger exhaustion]
\label{thm:cauchy-limit-seal-seal-ledger-exhaustion}
The carrier of \autoref{def:cauchy-limit-seal-carrier}, the $\NameCert_{\CauchyLimitSealUp}$ obligations, regular-source stability, diagonal-row compatibility, the $\RealUp$ consumer boundary, and the non-escape theorem exhaust the finite seal ledger for downstream $\RealUp$ and completion consumers. No further $\mathsf{BHist}$ row is available beyond the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ coordinates.
\end{theorem}
\begin{proof}
Start with the carrier projection. Its finite packet lists exactly the regular source family, schedule, observation ledger, diagonal completion row, real seal row, transport rows, package provenance, and local certificate.

Apply the $\NameCert$ obligations of \autoref{thm:cauchy-limit-seal-namecert-obligations}. They supply habitation, classifier stability, exact finite-route factorization, and the exclusion of quotient, host-limit, uniqueness, and ambient-completeness data.

Next combine \autoref{thm:cauchy-limit-seal-regular-source-stability} and \autoref{thm:cauchy-limit-seal-diagonal-row-compatibility}. The first keeps classifier transport on the displayed source, schedule, ledger, diagonal, and seal rows; the second prevents a downstream completion read from replacing the diagonal row by an object outside the packet.

Finally use the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary} and the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape}. These identify the public endpoint and rule out every listed hidden field, so the finite rows named in the statement exhaust the seal ledger for downstream real and completion consumers.
\end{proof}

\begin{theorem}[CauchyLimitSeal scheduled-window pullback]
\label{thm:cauchy-limit-seal-scheduled-window-pullback}
Let $L=(X,S,D,G,E,T,P,N)$ be an accepted $\CauchyLimitSealUp$ carrier. Any downstream predicate read on the sealed $\RealUp$ endpoint $E$ pulls back uniquely to a scheduled $\StreamNameUp$ finite window in $S$, its $\RegSeqRatUp$ row in $X$, the matching $\DyadicRatCoreUp$ observation row in $D$, and the displayed $\hsame$ and $\Cont$ transport rows in $T$. This pullback is a projection of the finite $\mathsf{BHist}$ packet named by $P$ and $N$, and it has no host-limit coordinate, quotient-stream coordinate, or independent completeness coordinate.
\end{theorem}
\begin{proof}
Project the carrier coordinates $X,S,D,G,E,T,P,N$. The endpoint $E$ is not stored as a free real object; it is the seal row reached through the scheduled route carried by the same finite $\mathsf{BHist}$ packet.

Apply the window factorization of \autoref{thm:cauchy-limit-seal-window-factorization}. A read on $E$ must pass through one scheduled $\StreamNameUp$ window from $S$, then through its $\RegSeqRatUp$ source row in $X$, and then through the corresponding $\DyadicRatCoreUp$ ledger row in $D$.

The remaining movement is exactly the transport ledger $T$. The stored $\hsame$ and $\Cont$ rows identify the admissible route from the scheduled observation to the completion row $G$ and the seal row $E$, while $P$ and $N$ name the dependency package and local $\NameCert$.

Uniqueness is componentwise in the displayed packet. Since no additional carrier coordinate contains a host limit, quotient stream, or ambient completeness datum, a downstream predicate on $E$ has only the scheduled finite-window pullback just described.
\end{proof}

\begin{theorem}[CauchyLimitSeal dyadic observation replay]
\label{thm:cauchy-limit-seal-dyadic-observation-replay}
For an accepted $\CauchyLimitSealUp$ carrier $L=(X,S,D,G,E,T,P,N)$, replaying any consumer read through the seal consumes exactly the displayed $\DyadicRatCoreUp$ observation ledger $D$ together with the $\Pkg$ provenance $P$ and the local $\NameCert$ row $N$. The replay does not consume an external tolerance, a hidden tail witness, a quotient-stream comparison, or a selected host limit.
\end{theorem}
\begin{proof}
Start with the finite route of \autoref{thm:cauchy-limit-seal-window-factorization}. The consumer read is routed from $S$ and $X$ into the observation ledger $D$ before it reaches the completion diagonal and the seal.

The replay step is therefore a ledger projection. Each dyadic observation used by the consumer is one of the displayed $\DyadicRatCoreUp$ rows in $D$, and its admissibility is recorded by the package provenance $P$ and the local certificate $N$.

Use the non-escape theorem \autoref{thm:cauchy-limit-seal-non-escape}. The carrier contains no external tolerance field, no hidden tail witness, no quotient-stream comparison, and no selected host-limit row. Hence the replay consumes exactly $D$, $P$, and $N$ along the visible $\mathsf{BHist}$, $\hsame$, and $\Cont$ route.
\end{proof}

\begin{theorem}[CauchyLimitSeal completion-consumer exactness]
\label{thm:cauchy-limit-seal-completion-consumer-exactness}
Every completion-facing consumer of accepted $\CauchyLimitSealUp$ carriers has the exact finite route obtained by composing the scheduled-window pullback of \autoref{thm:cauchy-limit-seal-scheduled-window-pullback}, the dyadic replay of \autoref{thm:cauchy-limit-seal-dyadic-observation-replay}, the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff}, and the null-sequence factorization of \autoref{thm:cauchy-limit-seal-nullsequence-factorization}. The route is wholly contained in the carrier coordinates $X,S,D,G,E,T,P,N$ and their visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
First pull the completion-facing read back from the sealed endpoint. By \autoref{thm:cauchy-limit-seal-scheduled-window-pullback}, the read lands on a scheduled finite window, its regular rational source row, the dyadic observation row, and the displayed transport rows.

Next replay the dyadic observation. By \autoref{thm:cauchy-limit-seal-dyadic-observation-replay}, the consumer uses exactly the displayed $\DyadicRatCoreUp$ ledger with the package provenance and local naming row, rather than any external tolerance or hidden tail witness.

Now apply the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff}. It keeps the completion consumer on the same source row, scheduled window, observation ledger, diagonal row, and seal route.

Finally use the null-sequence factorization of \autoref{thm:cauchy-limit-seal-nullsequence-factorization} when the consumer compares two sealed reads. The comparison attaches only the displayed $\NullSequenceUp$ tolerance-window-threshold packet to the already fixed route, so the completion consumer receives exactly the finite path through $X,S,D,G,E,T,P,N$ and the visible $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{proof}

\begin{theorem}[CauchyLimitSeal public route exhaustion]
\label{thm:cauchy-limit-seal-public-route-exhaustion}
Every public $\CauchyLimitSealUp$ route available to a downstream $\RealUp$ or completion-facing consumer is exhausted by the displayed $\RegSeqRatUp$ source row, $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ observation ledger, $\RealCauchyCompletionUp$ diagonal row, $\RealUp$ seal row, $\mathsf{BHist}$ packet, $\hsame$ and $\Cont$ transports, $\Pkg$ provenance, and local $\NameCert$ row. No public route can read a quotient stream, selected host limit, hidden tail witness, or ambient completeness coordinate outside those carrier rows.
\end{theorem}
\begin{proof}
Project the accepted carrier $L=(X,S,D,G,E,T,P,N)$ from \autoref{def:cauchy-limit-seal-carrier}. The only public rows named by the packet are the regular source, schedule, dyadic ledger, diagonal completion row, real seal, transport ledger, package row, and local certificate.

Use the scheduled-window pullback of \autoref{thm:cauchy-limit-seal-scheduled-window-pullback} and the dyadic replay of \autoref{thm:cauchy-limit-seal-dyadic-observation-replay}. These identify any consumer read with a scheduled finite window, its regular rational source row, the corresponding dyadic observation, and the stored transport route.

Now apply the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary} and the non-escape theorem of \autoref{thm:cauchy-limit-seal-non-escape}. They leave no coordinate for quotient streams, selected host limits, hidden tail witnesses, or ambient completeness data, so the displayed rows exhaust the public route.
\end{proof}

\begin{theorem}[CauchyLimitSeal pullback determinacy]
\label{thm:cauchy-limit-seal-pullback-determinacy}
Let two completion pullbacks of accepted $\CauchyLimitSealUp$ carriers use the same scheduled $\StreamNameUp$ window and the same $\DyadicRatCoreUp$ observation ledger inside the displayed carrier packet. Then they determine the same seal route through the $\RegSeqRatUp$ source, $\RealCauchyCompletionUp$ diagonal row, $\RealUp$ seal, $\hsame$ and $\Cont$ transport rows, $\Pkg$ provenance, and $\NameCert$ row. The pullback cannot introduce a quotient stream, a selected host limit, or an independent completion object.
\end{theorem}
\begin{proof}
Begin with the scheduled-window pullback. Once the $\StreamNameUp$ window and $\DyadicRatCoreUp$ ledger row are fixed, \autoref{thm:cauchy-limit-seal-scheduled-window-pullback} fixes the corresponding $\RegSeqRatUp$ source row and the displayed transport rows in the carrier.

Use diagonal-row compatibility from \autoref{thm:cauchy-limit-seal-diagonal-row-compatibility}. The completion read tied to that scheduled window and ledger must pass through the carrier diagonal row $G$, so it cannot be replaced by a separate completion object.

Finally apply the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff} and the public route exhaustion of \autoref{thm:cauchy-limit-seal-public-route-exhaustion}. The same fixed window and ledger therefore force the same route through the seal and leave no quotient-stream or selected-host-limit coordinate to distinguish another pullback.
\end{proof}

\begin{theorem}[CauchyLimitSeal standard boundary package]
\label{thm:cauchy-limit-seal-standard-boundary-package}
The window factorization, $\RealUp$ consumer boundary, downstream completion handoff, null-sequence factorization, public route exhaustion, and pullback determinacy assemble the standard boundary package for $\CauchyLimitSealUp$. The package presents the public seal route over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, and it exports no host-limit, quotient-completion, ambient-completeness, or hidden-tail premise.
\end{theorem}
\begin{proof}
First combine the window factorization of \autoref{thm:cauchy-limit-seal-window-factorization} with the $\RealUp$ consumer boundary of \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}. These rows route every public read from the schedule and regular source through the dyadic ledger, completion diagonal, transport rows, and seal.

Next attach the downstream completion handoff of \autoref{thm:cauchy-limit-seal-downstream-completion-handoff}. It identifies the completion-facing side of the same route and prevents an independent completeness principle or completion object from entering the packet.

For equality-facing reads, use the null-sequence factorization of \autoref{thm:cauchy-limit-seal-nullsequence-factorization}. It adds only the displayed $\NullSequenceUp$ tolerance-window-threshold packet to the already fixed seal route.

Finally apply public route exhaustion and pullback determinacy from \autoref{thm:cauchy-limit-seal-public-route-exhaustion} and \autoref{thm:cauchy-limit-seal-pullback-determinacy}. The assembled rows give the standard boundary package because they exhaust the public carrier surface and determine each completion pullback from the displayed schedule and dyadic ledger.
\end{proof}

\begin{theorem}[CauchyLimitSeal uniform-criterion pullback]
\label{thm:cauchy-limit-seal-uniform-criterion-pullback}
Let an accepted $\CauchyLimitSealUp$ carrier present a sealed $\RealUp$ read
whose source family is governed by an accepted $\UniformCauchyCriterionUp$
packet. Then the sealed read pulls back through the same scheduled
$\StreamNameUp$ windows, the same $\DyadicRatCoreUp$ observation row, the same
$\RegSeqRatUp$ source row, and the same $\RealCauchyCompletionUp$ diagonal row
used by the seal carrier. The pullback consumes the uniform family evidence
only through its finite family ledger, shared window family, uniform modulus,
dyadic tolerance, tail ledger, seal handoff, and visible $\mathsf{BHist}$,
$\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project the accepted $\CauchyLimitSealUp$ carrier. By
\autoref{thm:cauchy-limit-seal-scheduled-window-pullback}, every sealed read
on the $\RealUp$ endpoint pulls back to a scheduled $\StreamNameUp$ finite
window, its $\RegSeqRatUp$ source row, the matching $\DyadicRatCoreUp$
observation row, and the displayed transport route.

Now project the accepted $\UniformCauchyCriterionUp$ packet. Its
\autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness} route reads the
finite family ledger, shared window family, uniform modulus, dyadic tolerance,
and tail ledger before any real-facing seal handoff is consumed.

The two projections meet at the shared scheduled windows and dyadic
observation row. The CauchyLimitSeal diagonal row remains the displayed
$\RealCauchyCompletionUp$ coordinate, while the uniform criterion contributes
only the finite family-tail evidence attached to those same windows.

Finally use \autoref{thm:uniform-cauchy-criterion-non-escape-boundary}. The
uniform packet has no quotient stream family, selected family limit, host real
equality, or ambient completeness coordinate, so the pullback stays inside the
sealed finite route.
\end{proof}

\begin{theorem}[CauchyLimitSeal uniform tail seal route]
\label{thm:cauchy-limit-seal-uniform-tail-seal-route}
For any accepted $\CauchyLimitSealUp$ carrier whose source family is certified
by an accepted $\UniformCauchyCriterionUp$ packet, the route from family-tail
evidence to the sealed $\RealUp$ row factors through the shared family index,
the shared $\StreamNameUp$ window family, the uniform $\CauchyModulusUp$
schedule, the $\DyadicRatCoreUp$ tolerance row, the finite tail ledger, the
$\RealCauchyCompletionUp$ diagonal row, and the $\RealUp$ seal. The composed
route is exactly the composition of the CauchyLimitSeal window factorization,
the $\RealUp$ consumer boundary, and the UniformCauchyCriterion tail-ledger
exactness surface.
\end{theorem}
\begin{proof}
First apply \autoref{thm:uniform-cauchy-criterion-tail-ledger-exactness}. It
forces every accepted family-tail comparison through the family index, shared
window family, uniform modulus, dyadic tolerance, and finite tail ledger.

Next apply \autoref{thm:cauchy-limit-seal-window-factorization}. The seal
carrier reads the same scheduled window through the regular source row, the
dyadic observation ledger, the completion diagonal row, and the displayed
transport ledger before it reaches the seal.

Now attach \autoref{thm:cauchy-limit-seal-realup-consumer-boundary}. A
$\RealUp$ consumer may read the result only after the displayed finite-window
route has passed through the diagonal row and the seal row.

The composed route therefore has no branch outside the shared family index,
uniform modulus, tolerance row, tail ledger, diagonal row, and seal. Package
and local naming provenance are carried by the two packets' $\Pkg$ and
$\NameCert$ rows.
\end{proof}

\begin{theorem}[CauchyLimitSeal family seal non-escape]
\label{thm:cauchy-limit-seal-family-seal-non-escape}
The composed seal route of
\autoref{thm:cauchy-limit-seal-uniform-tail-seal-route} exports no quotient
stream family, no selected family limit, no ambient completeness principle, no
host real equality, and no hidden tail witness. Its public surface is exactly
the displayed $\UniformCauchyCriterionUp$ family-tail packet together with the
displayed $\CauchyLimitSealUp$ schedule, observation, diagonal, transport,
package, and local naming rows.
\end{theorem}
\begin{proof}
Start with the uniform side. By
\autoref{thm:uniform-cauchy-criterion-non-escape-boundary}, an accepted
$\UniformCauchyCriterionUp$ carrier exports only the family index ledger,
shared windows, uniform modulus, dyadic tolerance, finite tail ledger, seal
handoff, and visible kernel provenance rows.

Now read the seal side. The CauchyLimitSeal non-escape boundary of
\autoref{thm:cauchy-limit-seal-non-escape} removes quotient streams, selected
host limits, hidden tail witnesses, uniqueness theorems, and ambient
completeness data from the sealed route.

Finally combine the two boundaries through
\autoref{thm:cauchy-limit-seal-uniform-criterion-pullback} and
\autoref{thm:cauchy-limit-seal-uniform-tail-seal-route}. The pullback and
tail route share the same windows, tolerance row, tail ledger, diagonal row,
and seal, so no excluded coordinate can be introduced between the two packets.
\end{proof}

\closureat{CauchyLimitSealUp}{seedStr}
\closureat{CauchyLimitSealUp}{obligationStr}
\closureat{CauchyLimitSealUp}{scopedStr}
\closureat{CauchyLimitSealUp}{publicStr}

\begin{closurestatus}{\CauchyLimitSealUp}
  \constructivestory{A $\CauchyLimitSealUp$ packet is generated from a displayed $\RegSeqRatUp$ family, a $\StreamNameUp$ schedule, a $\DyadicRatCore$ observation ledger, a $\RealCauchyCompletionUp$ diagonal row, a $\RealUp$ seal row, finite $\hsame$ and $\Cont$ transports, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The scoped surface is exactly the carrier, classifier transport, finite-window factorization, non-escape boundary, and $\RealUp$ consumer boundary over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close quotient Cauchy completion, uniqueness of limits, host real construction, ambient real completeness, or bridge checking.}
  \upgradepath{The next paper grade is a bridge from the public sealed $\RealUp$ boundary to the abstract $\CauchyLimitSealUp$ interface.}
\end{closurestatus}
