\begin{theorem}[CauchyLimitSeal tail extraction]
\label{thm:cauchy-limit-seal-tail-extraction}
Every admitted tail read of an accepted $\CauchyLimitSealUp$ packet is projected from the displayed $\RegSeqRatUp$ family, $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ observation ledger, $\RealCauchyCompletionUp$ diagonal row, and visible $\hsame$ and $\Cont$ ledger. The projection is the same public route consumed by the seal packet, not a tail chosen from a quotient stream, host limit, hidden family limit, or ambient completeness principle.
\end{theorem}
\begin{proof}
Begin with family-tail admission. By \autoref{thm:cauchy-limit-seal-family-tail-admission}, a tail read is admitted only with the displayed source family, schedule, tail modulus, null-tail comparison, completion diagonal, seal row, transports, route, provenance, and local naming row.

Next attach seal-window ledger compatibility from \autoref{thm:cauchy-limit-seal-seal-window-ledger-compatibility}. The admitted tail therefore uses the same scheduled window and dyadic observation ledger as the seal route.

Finally pull the observation budget back along \autoref{thm:cauchy-limit-seal-observation-budget-pullback}. The tail read is projected through the displayed regular family, schedule, dyadic ledger, diagonal row, and visible $\hsame$ and $\Cont$ route, with no remaining coordinate for an external tail source.
\end{proof}

\begin{theorem}[CauchyLimitSeal uniqueness boundary]
\label{thm:cauchy-limit-seal-uniqueness-boundary}
Every equality or uniqueness-facing consumer of an accepted $\CauchyLimitSealUp$ packet may use only the visible null-sequence and tail-comparison route. It cannot import a host uniqueness theorem, quotient-stream equality, selected limit, hidden family limit, or ambient completeness datum.
\end{theorem}
\begin{proof}
Start with the non-escape boundary of \autoref{thm:cauchy-limit-seal-non-escape}. The accepted packet contains no host uniqueness theorem, quotient representative, selected limit, or ambient completeness coordinate.

For the comparison itself, use null-sequence factorization from \autoref{thm:cauchy-limit-seal-nullsequence-factorization}. Equality-facing reads can add only the displayed $\NullSequenceUp$ tolerance-window-threshold row to the already fixed seal route.

Then apply budgeted tail comparison admission from \autoref{thm:cauchy-limit-seal-budgeted-tail-comparison-admission}. A uniqueness-facing read is therefore admitted only through the same finite budget, scheduled window, dyadic ledger, regular handoff, seal, transport, route, provenance, and naming rows.
\end{proof}

\begin{theorem}[CauchyLimitSeal consumer readback]
\label{thm:cauchy-limit-seal-consumer-readback}
A downstream $\RealUp$ or completion consumer reads back exactly the sealed route assembled by the root-unblock package, together with the tail-extraction row of \autoref{thm:cauchy-limit-seal-tail-extraction} and the uniqueness boundary of \autoref{thm:cauchy-limit-seal-uniqueness-boundary}. The readback exports only the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Apply the root-unblock package of \autoref{thm:cauchy-limit-seal-root-unblock-package}. It gives the consumer one route from the accepted seal packet to the downstream $\RealUp$ or completion boundary.

Attach tail extraction. The tail row is already projected from the same displayed regular family, schedule, observation ledger, completion diagonal, and transport ledger, so it does not add a second consumer route.

Finally attach the uniqueness boundary. Equality-facing reads remain on the null-sequence and tail-comparison route admitted by the packet, and the readback has no coordinate for quotient completion, host uniqueness, selected limits, hidden family limits, or ambient completeness.
\end{proof}
