\begin{theorem}[CauchyLimitSeal consumer readback]
\label{thm:cauchy-limit-seal-consumer-readback}
A downstream $\RealUp$ or completion consumer reads back exactly the sealed route assembled by the root-unblock package, together with the tail-extraction row of \autoref{thm:cauchy-limit-seal-tail-extraction} and the uniqueness boundary of \autoref{thm:cauchy-limit-seal-uniqueness-boundary}. The readback exports only the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\end{theorem}
\begin{proof}
Apply the root-unblock package of \autoref{thm:cauchy-limit-seal-root-unblock-package}. It gives the consumer one route from the accepted seal packet to the downstream $\RealUp$ or completion boundary.

Attach tail extraction. The tail row is already projected from the same displayed regular family, schedule, observation ledger, completion diagonal, and transport ledger, so it does not add a second consumer route.

Finally attach the uniqueness boundary. Equality-facing reads remain on the null-sequence and tail-comparison route admitted by the packet, and the readback has no coordinate for quotient completion, host uniqueness, selected limits, hidden family limits, or ambient completeness.
\end{proof}

\begin{theorem}[CauchyLimitSeal RegSeqRat StreamName route lock]
\label{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}
Every accepted $\CauchyLimitSealUp$ packet consumed by a $\RealUp$ or completion-facing route factors through the displayed $\StreamNameUp$ finite window of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the $\DyadicRatCoreUp$ tolerance ledger of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the $\RealUp$ seal row of \autoref{ch:concrete-instances-real-namecert}, and the $\RealCauchyCompletionUp$ consumer boundary of \autoref{ch:concrete-instances-real-cauchy-completion-namecert}. The factorization uses only the displayed $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows already exposed by the accepted seal route.

Consequently the accepted consumer route exports no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completion row, or standard bridge row outside that finite L10 route.
\end{theorem}
\begin{proof}
Start with the consumer readback theorem, \autoref{thm:cauchy-limit-seal-consumer-readback}. It confines every downstream $\RealUp$ or completion consumer to the accepted seal packet, its root-unblock route, tail-extraction row, uniqueness boundary, and the displayed $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealCauchyCompletionUp$, and $\RealUp$ rows.

Next attach the finite route theorems already exposed on the Real side. The four-face canonical route of \autoref{thm:real-l10-four-face-canonical-route} and the seal lattice of \autoref{thm:real-streamname-regseqrat-seal-lattice} force any completion-facing $\RealUp$ consumer carrying a $\CauchyLimitSealUp$ row through the ordered $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, and $\RealUp$ faces before the seal row is read.

Finally use the terminal comparison exhaustion of \autoref{thm:real-l10-terminal-comparison-exhaustion} together with the $\RealCauchyCompletionUp$ consumer boundary cited above. These rows keep the completion-facing endpoint on the same displayed histories, transports, continuations, provenance, and local names, so no quotient stream, host sequence equality, selected limit, ambient completeness, metric-completion coordinate, or standard bridge coordinate remains available to the consumer.
\end{proof}

\begin{theorem}[Real-completion seal selector consumer factorization]
\label{thm:real-completion-seal-selector-consumer-factorization}
Let an accepted $\CauchyLimitSealUp$ consumer be routed through an accepted $\RealCompletionSelectorSealUp$ packet and an accepted $\ObserverFilterBudgetSelectorUp$ budget packet for the current Real and Completion handoff. Then its consumer read factors through the concrete displayed chain
$$
\ObserverFilterBudgetSelectorUp \to \StreamNameUp \to \DyadicRatCoreUp \to \RegSeqRatUp \to \CauchyLimitSealUp \to \RealUp.
$$
The factorization uses only the visible $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows of the three accepted packets. It exports no quotient stream, host real equality, hidden selector, detached limit, or ambient completeness coordinate.
\end{theorem}
\begin{proof}
Start with the route lock of \autoref{thm:cauchy-limit-seal-regseqrat-streamname-route-lock}. It confines the $\CauchyLimitSealUp$ consumer to the displayed $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\CauchyLimitSealUp$, and $\RealUp$ rows, with only $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ support.

Next attach the selector-seal packet. The L10 handoff scope of \autoref{thm:real-completion-selector-seal-l10-handoff-scope} identifies the selector-seal consumer as the same finite route through selector budget, selected window, regular readback, limit-seal handoff, and terminal $\RealUp$ endpoint.

Finally attach the observer-budget packet. The bridge-ready route of \autoref{thm:observer-filter-budget-selector-bridge-ready-route} supplies the selected observer row, finite budget, selected $\StreamNameUp$ window, dyadic ledger, regular handoff, and Real seal in that order. Combining the three displayed routes gives the stated factorization, and the coordinate exclusions in the cited theorems leave no quotient stream, host real equality, hidden selector, detached limit, or ambient completeness row for the consumer.
\end{proof}
