\chapter{A Concrete Naming Certificate for $\FoldMomentKernelUp$}
\label{ch:concrete-instances-fold-moment-kernel-namecert}
\origin{ai}

Inspired by Omega Project: \texttt{automath/README.md/Fiber Spectrum and Moment Theory}; here re-expressed in the BEDC mathlib-free substrate.

The $\FoldMomentKernelUp$ interface names a finite collision-moment packet for
folded fibers. It records only visible $\mathsf{BHist}$ rows for a finite
window, fold sources, fiber ledgers, moment indices, collision counts,
transport routes, continuation routes, package provenance, and local
$\NameCert$ evidence. It does not import analytic spectral data, host counting
semantics, quotient fibers, or an external measure space.

\begin{definition}[FoldMomentKernel carrier]
\label{def:fold-moment-kernel-carrier}
A $\FoldMomentKernelUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
K=(W,F,L,I,Q,T,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $W$ is the finite window row naming the inspected source and target
positions;
\item $F$ is the fold-source row recording the displayed finite sources whose
images are compared in the window;
\item $L$ is the visible fiber ledger listing the inspected source entries
above each displayed target entry;
\item $I$ is the moment-index row naming the finite family of moment requests
read by consumers;
\item $Q$ is the collision-count row family, with one displayed finite count
ledger for each inspected target and moment index;
\item $T$ records componentwise $\hsame$ transports for windows, fold sources,
fiber ledgers, moment indices, and collision-count rows;
\item $C$ records the displayed $\Cont$ routes by which consumers reach the
window, fold-source, fiber-ledger, moment-index, and collision-count rows;
\item $P$ is the $\Pkg$ provenance naming the finite BEDC packets that own the
source window, target window, fold relation, ledger rows, and count rows;
\item $N$ is the local $\NameCert_{\FoldMomentKernelUp}$ row.
\end{enumerate}
The carrier contains no host cardinality function, no analytic spectrum, no
ambient probability measure, and no quotient of fibers.
\end{definition}
\leandef{BEDC.Derived.FoldMomentKernelUp.FoldMomentKernelUp}
\leanchecked{BEDC.Derived.FoldMomentKernelUp.FoldMomentKernelTasteGate\_single\_carrier\_alignment}
\leandef{BEDC.Derived.FoldMomentKernelUp.taste\_gate}

\begin{definition}[FoldMomentKernel classifier]
\label{def:fold-moment-kernel-classifier}
For accepted $\FoldMomentKernelUp$ carriers $K$ and $K'$, the classifier
$\mathsf{FoldMomentKernelClassifier}(K,K')$ compares only the displayed window
rows, fold-source rows, fiber-ledger rows, moment-index rows, collision-count
rows, componentwise $\hsame$ transports, $\Cont$ read routes, $\Pkg$
provenance, and local $\NameCert$ evidence of
\autoref{def:fold-moment-kernel-carrier}.

The classifier does not compare hidden source sets, host counts, analytic
moments, spectral values, quotient fibers, or unrecorded fold laws.
\end{definition}

\begin{theorem}[FoldMomentKernel zero-window packet]
\label{thm:fold-moment-kernel-zero-window-packet}
The empty source window with the zero target window determines an accepted
$\FoldMomentKernelUp$ carrier. Its fold-source row is empty, its visible fiber
ledger has no source entries, every moment-index read is represented by the
displayed zero row, every collision-count row is zero, and all transport,
continuation, package, and local naming rows are the corresponding finite
identity rows.
\end{theorem}
\leanchecked{BEDC.Derived.FoldMomentKernelUp.FoldMomentKernelUp\_zero\_window\_packet}
\leanvariant{BEDC.Derived.FoldMomentKernelUp.FoldMomentKernelZeroWindowPacket}
\begin{proof}
Start with the empty displayed window. There are no source entries to fold and
no target fiber entries to inspect, so the fiber ledger is the empty finite
ledger.

For each moment index carried by the packet, use the zero collision-count row.
The count row is visible data in $Q$, not a host cardinality computation.

The transport and continuation routes are componentwise identity routes on the
empty and zero rows. Repacking them with the package provenance and local
certificate row gives the stated carrier.
\end{proof}

\begin{theorem}[FoldMomentKernel NameCert obligation surface]
\label{thm:fold-moment-kernel-namecert-obligation-surface}
The local $\NameCert_{\FoldMomentKernelUp}$ obligation surface consists of five
rows:
\begin{enumerate}
\item carrier inhabitation: \autoref{thm:fold-moment-kernel-zero-window-packet}
supplies the empty-source and zero-window packet;
\item classifier transport: \autoref{def:fold-moment-kernel-classifier}
transports windows, fold-source rows, fiber ledgers, moment indices,
collision-count rows, $\hsame$ routes, $\Cont$ routes, package provenance, and
local provenance componentwise;
\item fiber-ledger exactness: every visible source entry counted by the packet
appears in the displayed fiber ledger $L$, and every ledger entry is tied to the
displayed fold-source row $F$ and window row $W$;
\item moment readback boundary: every moment read factors through $I$, $Q$,
$L$, $T$, $C$, $P$, and $N$ before reaching any downstream consumer;
\item non-escape: the packet exports no host counting operation, analytic
moment, spectral theorem, quotient fiber, ambient measure, or unrecorded
fold-completeness claim.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FoldMomentKernelUp.FoldMomentKernelTasteGate\_visible\_rows}
\begin{proof}
The carrier row is the finite packet of
\autoref{def:fold-moment-kernel-carrier}, and
\autoref{thm:fold-moment-kernel-zero-window-packet} gives a concrete
inhabitant. Thus the local certificate has an admitted finite source surface.

Classifier transport is componentwise by
\autoref{def:fold-moment-kernel-classifier}. A displayed $\hsame$ transport can
move only window, fold-source, fiber-ledger, moment-index, collision-count,
route, provenance, and local certificate rows already present in the packet.

Fiber-ledger exactness is obtained by projecting $L$ together with $F$ and $W$.
Every counted source entry is read from that ledger, and every ledger entry is
attached to the displayed fold-source and window rows by the recorded
continuation routes.

Moment readback is a boundary statement about the visible rows $I$ and $Q$.
The consumer can inspect the requested moment only through the moment-index row,
the associated collision-count ledger, the fiber ledger, transports,
continuations, package provenance, and local certificate row.

Since those rows exhaust the carrier coordinates, there is no remaining field
from which host counting, analytic spectral information, quotient fibers,
ambient measure, or a hidden completeness principle could be exported.
\end{proof}

\closureat{FoldMomentKernelUp}{seedStr}

\begin{closurestatus}{\FoldMomentKernelUp}
  \constructivestory{A $\FoldMomentKernelUp$ packet is generated from finite window rows, fold-source rows, visible fiber ledgers, moment-index rows, collision-count rows, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope fixes the finite carrier, classifier, zero-window inhabitant, fiber-ledger exactness row, moment readback boundary, and non-escape obligations for collision-moment packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close analytic spectra, host cardinality, quotient fibers, ambient measure theory, collision asymptotics, or bridge checking.}
  \upgradepath{Scoped closure requires checked transport stability, fiber-ledger exactness, moment readback totality, and public finite-packet export for the same carrier.}
\end{closurestatus}

\begin{theorem}[FoldMomentKernel finite-window restriction carrier]
\label{thm:fold-moment-kernel-finite-window-restriction-carrier}
Let
$$
K=(W,F,L,I,Q,T,C,P,N)
$$
be an accepted $\FoldMomentKernelUp$ carrier, and let $\Omega$ be a displayed
finite subwindow of the window row $W$. Suppose the packet has coherent
restriction rows
$$
W_{\Omega},F_{\Omega},L_{\Omega},I_{\Omega},Q_{\Omega},T_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega}
$$
with the following properties:
\begin{enumerate}
\item $W_{\Omega}$ is the selected finite source-and-target subwindow of $W$;
\item $F_{\Omega}$ contains exactly the fold-source entries of $F$ whose
visible source or target addresses lie in $W_{\Omega}$;
\item $L_{\Omega}$ contains exactly the fiber-ledger entries of $L$ above the
displayed target entries of $W_{\Omega}$ and using fold sources from
$F_{\Omega}$;
\item $I_{\Omega}$ is the displayed finite family of moment requests retained
for the subwindow;
\item $Q_{\Omega}$ contains exactly the collision-count ledgers of $Q$ whose
target and moment-index addresses lie in $W_{\Omega}$ and $I_{\Omega}$;
\item $T_{\Omega}$ and $C_{\Omega}$ are the componentwise restrictions of the
$\hsame$ transport rows and $\Cont$ read routes whose endpoints are among
$W_{\Omega}$, $F_{\Omega}$, $L_{\Omega}$, $I_{\Omega}$, and $Q_{\Omega}$;
\item $P_{\Omega}$ names precisely the package provenance rows consumed by the
retained window, fold-source, ledger, moment-index, and count rows;
\item $N_{\Omega}$ is the local $\NameCert_{\FoldMomentKernelUp}$ row restricted
to those same retained coordinates.
\end{enumerate}
Then
$$
K_{\Omega}=(W_{\Omega},F_{\Omega},L_{\Omega},I_{\Omega},Q_{\Omega},T_{\Omega},C_{\Omega},P_{\Omega},N_{\Omega})
$$
is an accepted $\FoldMomentKernelUp$ carrier.
\end{theorem}
\begin{proof}
Unfold the carrier of \autoref{def:fold-moment-kernel-carrier}. A
$\FoldMomentKernelUp$ carrier has only the nine displayed coordinates
$$
W,F,L,I,Q,T,C,P,N.
$$
The hypotheses provide a retained row for each of these coordinates over the
finite subwindow $\Omega$. Thus $K_{\Omega}$ has the required window,
fold-source, fiber-ledger, moment-index, collision-count, transport,
continuation, provenance, and local naming entries.

The fiber and count rows remain well-formed because the restriction is
coordinatewise coherent. Every source entry in $L_{\Omega}$ is one already
listed by the retained fold-source row $F_{\Omega}$, and every retained count
row in $Q_{\Omega}$ is indexed by a retained target entry of $W_{\Omega}$ and a
retained moment request of $I_{\Omega}$. Conversely, the hypotheses discard only
rows whose visible addresses lie outside the selected subwindow, so no retained
ledger entry loses its displayed source, target, or moment-index address.

The transport and readback rows also remain internal to the restricted packet.
By the classifier scope of \autoref{def:fold-moment-kernel-classifier}, a
$\mathsf{FoldMomentKernelClassifier}$ comparison may inspect only displayed
window rows, fold-source rows, fiber-ledger rows, moment-index rows,
collision-count rows, componentwise $\hsame$ transports, $\Cont$ routes,
package provenance, and local $\NameCert$ evidence. The rows $T_{\Omega}$ and
$C_{\Omega}$ are exactly the retained transports and routes with endpoints in
those restricted coordinates, so every classifier or consumer read in the
subwindow still factors through visible rows of $K_{\Omega}$.

Finally apply the obligation surface of
\autoref{thm:fold-moment-kernel-namecert-obligation-surface}. Carrier
inhabitation is supplied by the displayed restricted packet itself, classifier
transport is the componentwise restricted transport just described,
fiber-ledger exactness is the retained $F_{\Omega}$--$L_{\Omega}$--$W_{\Omega}$
incidence, moment readback factors through $I_{\Omega}$, $Q_{\Omega}$,
$L_{\Omega}$, $T_{\Omega}$, $C_{\Omega}$, $P_{\Omega}$, and $N_{\Omega}$, and
non-escape follows because \autoref{def:fold-moment-kernel-carrier} gives no
coordinate for host cardinality, analytic spectra, quotient fibers, ambient
measure, or unrecorded fold laws. Repacking these retained rows gives the
accepted carrier $K_{\Omega}$.
\end{proof}
