\chapter{A Concrete Naming Certificate for $\SocketStackCertificateUp$}
\label{ch:concrete-instances-socketstackcertificate-namecert}
\origin{ai}

The $\SocketStackCertificateUp$ packet realizes stacked socket reports from \autoref{subsec:philosophy-unity-transcendental-supply} as finite NameCert data. It sits beside the typed gap socket taxonomy of \autoref{ch:concrete-instances-typedgapsockettaxonomy-namecert}, the socket-kind classifier of \autoref{ch:concrete-instances-socketkindclassifier-namecert}, the socket taxonomy ledger of \autoref{ch:concrete-instances-socket-taxonomy-ledger-namecert}, the supply socket ledger of \autoref{ch:concrete-instances-supplysocketledger-namecert}, and the apophatic far-end socket of \autoref{ch:concrete-instances-apophaticfarendsocket-namecert}. Those siblings expose kind families, single-row classifiers, non-collapse accounting, requested-supply ledgers, and the common far-end boundary; this packet binds an ordered multi-socket stack without collapsing the component requests into one dominant kind.

\begin{definition}[Socket stack certificate carrier]
\label{def:socket-stack-certificate-carrier}
A $\SocketStackCertificateUp$ carrier is a finite $\BHist$ packet
$$
\Sigma=(Q,R,E,K,A,L,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $Q$ is the stack site row, naming the blocked proof, construction, or audit position whose requested supply has more than one socket component;
\item $R=(R_0,\ldots,R_n)$ is a nonempty ordered list of component socket-report rows, each carrying its site, requested-supply, narrow kind, and local gate;
\item $E$ is the stack-exposure row, recording that every component socket row is visible to audit consumers before any summary row is read;
\item $K=(K_0,\ldots,K_n)$ is the componentwise narrowest-kind classifier row, with $K_i$ classifying $R_i$ by the smallest socket kind licensed for that component;
\item $A=(A_0,\ldots,A_n)$ is the per-row audit-gate preservation row, requiring each component gate to be replayed at its own socket row;
\item $L$ is the non-discharge ledger route, recording that the stack reports requested supply without supplying any component row;
\item $H$ stores componentwise $\hsame$ transport for $Q,R,E,K,A,L,C,P,N$;
\item $C$ stores displayed $\Cont$ continuation from the stack site through the component reports, classifiers, gates, ledger route, provenance, and local name;
\item $P$ is the $\Pkg$ provenance over $\TypedGapSocketTaxonomyUp$, $\SocketKindClassifierUp$, $\SocketTaxonomyLedgerUp$, $\SupplySocketLedgerUp$, $\ApophaticFarEndSocketUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\SocketStackCertificateUp}$ row.
\end{enumerate}
The carrier has no coordinate for replacing the ordered component list by a single aggregate socket kind, deleting a component row after acceptance, moving a component gate to a sibling row, or treating the common far-end position as a discharge witness.
\end{definition}

\begin{theorem}[Socket stack certificate NameCert obligations]
\label{thm:socket-stack-certificate-namecert-obligations}
For the carrier of \autoref{def:socket-stack-certificate-carrier}, the local $\NameCert_{\SocketStackCertificateUp}$ surface consists exactly of carrier exposure for
$$
\Sigma=(Q,R,E,K,A,L,H,C,P,N),
$$
stack-site exposure through $Q$, ordered component socket exposure through $R$, stack exhaustion through $E$, componentwise narrowest-kind classification through $K$, per-row audit-gate preservation through $A$, non-discharge ledger routing through $L$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ continuation through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet $\Sigma=(Q,R,E,K,A,L,H,C,P,N)$. The stack site and the ordered component rows are read before classifier, gate, ledger, continuation, provenance, and naming rows, so the certificate cannot replace the stack by an uninspected summary.

Read $K$ and $A$ componentwise. Each $K_i$ names the narrow socket kind for the displayed component $R_i$, while each $A_i$ preserves the local gate attached to that same row. Componentwise transport in $H$ can replay these rows but cannot move a classifier or gate to a different component.

Finally inspect $L,C,P,N$. These rows account for the route, replay the same ordered packet, cite the sibling socket ledgers, and name the certificate. None supplies a requested component row, so the non-discharge route remains part of the local NameCert surface.
\end{proof}

\begin{theorem}[Socket stack certificate exhaustion]
\label{thm:socket-stack-certificate-stack-exhaustion}
Every accepted $\SocketStackCertificateUp$ packet exposes all component socket rows in its ordered carrier. Removing any component row from an accepted stack changes the componentwise classifier surface or breaks the $\NameCert$ handoff.
\end{theorem}
\begin{proof}
Let $\Sigma=(Q,R,E,K,A,L,H,C,P,N)$ be accepted. By \autoref{thm:socket-stack-certificate-namecert-obligations}, the exposure row $E$ is part of the local NameCert surface and is read against the ordered component list $R=(R_0,\ldots,R_n)$.

If a component row $R_i$ is removed, then the matching classifier row $K_i$ and gate row $A_i$ either become unmatched or must also be removed. In the first case, the componentwise classifier surface is no longer a well-formed stack surface. In the second case, the displayed packet named by $N$ is a different finite carrier.

Thus accepted stacks are exhausted by their displayed component rows. A shorter stack may be a separate packet, but it is not the same accepted $\SocketStackCertificateUp$ certificate.
\end{proof}

\begin{theorem}[Socket stack certificate sibling independence]
\label{thm:socket-stack-certificate-sibling-independence}
The $\SocketStackCertificateUp$ carrier is not bijective, under NameCert-row preservation, to $\TypedGapSocketTaxonomyUp$, $\SocketKindClassifierUp$, $\SocketTaxonomyLedgerUp$, $\SupplySocketLedgerUp$, or $\ApophaticFarEndSocketUp$.
\end{theorem}
\begin{proof}
Compare the displayed rows. $\TypedGapSocketTaxonomyUp$ carries the seven-kind taxonomy, $\SocketKindClassifierUp$ classifies a socket kind, $\SocketTaxonomyLedgerUp$ records taxonomy and non-collapse rows, $\SupplySocketLedgerUp$ accounts for requested supply, and $\ApophaticFarEndSocketUp$ names the common far-end boundary.

None of those siblings carries an ordered multi-socket component list with stack exposure, per-row narrowest-kind classifiers, per-row gate preservation, stack exhaustion, and a non-discharge ledger route. A NameCert-row-preserving bijection would have to preserve that joint ordered surface, so no listed sibling is bijective to $\SocketStackCertificateUp$.
\end{proof}

\falsifiablePrediction{Removing any component socket row from an accepted stack changes the componentwise classifier or breaks the NameCert handoff.}

\independenceWitness{typedgapsockettaxonomy, socketkindclassifier, sockettaxonomyledger, supplysocketledger, apophaticfarendsocket: none carries an ordered multi-socket carrier with per-row gate preservation and stack exhaustion.}

The Lean follow-up file for $\mathsf{BEDC.Derived.SocketStackCertificateUp}$ must provide explicit $\Nontrivial\ \SocketStackCertificateUp$ and $\FieldFaithful\ \SocketStackCertificateUp$ instances. The field-faithfulness witness must preserve $Q,R,E,K,A,L,H,C,P,N$ as distinct rows so a checked TasteGate theorem can rule out component deletion and single-kind collapse of an accepted stack.

\closureat{SocketStackCertificateUp}{seedStr}
\closureat{SocketStackCertificateUp}{obligationStr}

\begin{closurestatus}{\SocketStackCertificateUp}
  \constructivestory{The socket stack certificate is generated from $BHist$ rows that record an ordered multi-socket carrier, component socket rows, per-row gate preservation, and an exhaustion witness saying that the stack has been read as a stack. The carrier first names the stack packet, then checks that the stack rows are exhausted by the certificate, and finally allows $\Cont$ only to carry the same certified stack forward. The $hsame$ relation preserves the stack certificate across representative histories. NameCert obligations, stack exhaustion, sibling independence, prediction, and independence witness keep this object distinct from typed-gap taxonomy, socket-kind classifier, supply socket ledger, and apophatic far-end sockets.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the socket stack-certificate carrier, NameCert obligations, stack-exhaustion theorem, sibling-independence theorem, falsifiable prediction, and independence witness.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{It does not claim report classification, typed supply availability, phase-refusal verdicts, or stack equality outside the certified rows.}
  \upgradepath{Reaching obligationClosure requires formal stack rows and checked exhaustion plus sibling separation for the stack certificate.}
\end{closurestatus}
