\chapter{A Concrete Naming Certificate for $\DiagonalLimitUp$}
\label{ch:concrete-instances-diagonallimit-namecert}
\origin{human}

The $\DiagonalLimitUp$ packet names the concrete regular-Cauchy-family diagonal construction that sits above the finite diagonal selectors and below the $\RealUp$ consumer seal. Following the Bishop--Bridges constructive-analysis treatment of Cauchy completion, it keeps the inspected regular rational family, explicit modulus rows, stream windows, dyadic readback ledger, diagonal completion packet, and real seal as visible certificate data. It does not quotient regular streams, select a host limit, or import ambient real completeness.

The diagonal packet consumes the tail-comparison surface of \autoref{ch:concrete-instances-cauchy-tail-comparison-namecert} before its $\RealDiagonalCompletionUp$ and $\RealUp$ seal rows are read. The dependency is the finite modulus/window/tail-comparison ledger, not quotient stream equality or selected limit data.

\begin{definition}[DiagonalLimit regular-Cauchy-family carrier]
\label{def:diagonallimit-regular-cauchy-family-carrier}
A $\DiagonalLimitUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
L=(F,M,S,D,C,E,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $F$ is the $\RegSeqRatUp$-indexed regular Cauchy family whose inspected members are displayed as regular rational rows;
\item $M$ is the $\CauchyModulusUp$ row selecting a late enough family member for each requested consumer precision;
\item $S$ is the finite $\StreamNameUp$ schedule of windows read by the diagonal construction;
\item $D$ is the $\DyadicRatCoreUp$ observation ledger attached to the selected rational readbacks;
\item $C$ is the $\RealDiagonalCompletionUp$ packet that repacks the selected diagonal rows as a completion-facing finite surface;
\item $E$ is the $\RealUp$ seal row exposed to downstream consumers;
\item $P$ is the $\Pkg$ provenance naming the $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, and $\RealUp$ dependencies;
\item $N$ is the local $\NameCert_{\DiagonalLimitUp}$ provenance row.
\end{enumerate}
Two accepted packets are classified together exactly when the displayed family rows, modulus rows, stream windows, dyadic ledgers, diagonal-completion packets, real seals, package rows, and local certificate rows are transported componentwise by the recorded $\hsame$ comparisons and $\Cont$ routes.
\end{definition}
\leanchecked{BEDC.Derived.DiagonalLimitUp.DiagonalLimitTasteGate\_single\_carrier\_alignment}

\begin{theorem}[DiagonalLimit NameCert obligation surface]
\label{thm:diagonallimit-namecert-obligation-surface}
The local $\NameCert_{\DiagonalLimitUp}$ obligation surface consists of carrier habitation by the finite packet of \autoref{def:diagonallimit-regular-cauchy-family-carrier}, componentwise classifier transport through displayed $\hsame$ and $\Cont$ rows, diagonal regularity bounds over the explicit $\CauchyModulusUp$ row, handoff to $\RealDiagonalCompletionUp$ and $\RealUp$, and ledger non-escape over $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\mathsf{BHist}$, $\Pkg$, and $\NameCert$.
\end{theorem}
\begin{proof}
Carrier habitation is the packet assembly in \autoref{def:diagonallimit-regular-cauchy-family-carrier}. The visible rows name the regular Cauchy family, the modulus, the finite windows, the dyadic observations, the diagonal completion packet, the real seal, and the local provenance.

Classifier transport is componentwise. A permitted replacement is either an $\hsame$ comparison of one displayed row or a $\Cont$ route identifying where that row is read inside the finite packet, so transport preserves the same carrier boundary.

The remaining obligations are the diagonal regularity bound, the completion handoff, and non-escape boundary recorded in the following theorems. Together they list exactly the rows consumed by the local naming certificate.
\end{proof}

\begin{theorem}[DiagonalLimit diagonal regularity bound]
\label{thm:diagonallimit-diagonal-regularity-bound}
For every accepted $\DiagonalLimitUp$ carrier and every displayed unary precision request $n$, the modulus row $M$ selects a finite family member and a finite $\StreamNameUp$ window such that the selected $\RegSeqRatUp$ readback is bounded by the dyadic observation ledger $D$ at the requested precision. The bound is transported only through the packet's displayed $\hsame$ comparisons and $\Cont$ routes.
\end{theorem}
\begin{proof}
Project the accepted packet through \autoref{def:diagonallimit-regular-cauchy-family-carrier}. The precision request is answered by the explicit $\CauchyModulusUp$ coordinate, so the selected family member is a displayed row rather than a hidden limit choice.

The selected member is read through the finite $\StreamNameUp$ schedule. Its rational observation is recorded in the $\RegSeqRatUp$ family row and the accompanying $\DyadicRatCoreUp$ ledger.

Since the classifier transports only displayed rows through $\hsame$ and $\Cont$, the same bound follows after any accepted transport. No quotient stream or host real endpoint is used to obtain the bound.
\end{proof}

\begin{theorem}[DiagonalLimit Real-Cauchy handoff boundary]
\label{thm:diagonallimit-real-cauchy-handoff-boundary}
Every $\RealUp$ consumer read exported by an accepted $\DiagonalLimitUp$ packet factors through the same terminal precision, selected $\StreamNameUp$ window, $\RegSeqRatUp$ readback, $\DyadicRatCoreUp$ ledger, $\RealDiagonalCompletionUp$ packet, $\RealUp$ seal, visible $\hsame$ rows, visible $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\DiagonalLimitUp}$ row.
\end{theorem}
\begin{proof}
Begin with the selected diagonal window supplied by \autoref{thm:diagonallimit-diagonal-regularity-bound}. It exposes the precision, modulus-selected member, stream window, regular rational readback, and dyadic observation ledger.

The $\RealDiagonalCompletionUp$ coordinate $C$ repacks exactly those displayed rows as the completion-facing finite surface. The $\RealUp$ seal $E$ is attached to that same completion packet and not to an independent host real object.

Repacking the visible rows with the package and local certificate provenance gives the stated consumer handoff. The route has no coordinate for quotient equality, selected limits, uniqueness of limits, or ambient completeness.
\end{proof}

\begin{theorem}[DiagonalLimit non-escape boundary]
\label{thm:diagonallimit-non-escape-boundary}
An accepted $\DiagonalLimitUp$ packet exports only the displayed $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows. It exports no quotient of regular streams, no host real equality, no selected limit, no uniqueness theorem for limits, and no ambient real-completeness principle.
\end{theorem}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:diagonallimit-regular-cauchy-family-carrier}. Each coordinate is a displayed BEDC row or a local provenance row named in the packet.

The regularity theorem accounts for every precision-sensitive rational read, and the handoff theorem accounts for every $\RealUp$ consumer read. Thus every public route through the packet has already passed through visible finite data.

None of the carrier coordinates is a quotient class, a host-level equality witness, a selected limit object, a uniqueness theorem, or an ambient completeness field. Those objects cannot be recovered from the packet boundary.
\end{proof}

\begin{theorem}[DiagonalLimit obligation transport scope]
\label{thm:diagonallimit-obligation-transport-scope}
For any two accepted $\DiagonalLimitUp$ packets, accepted packet transport preserves the carrier of \autoref{def:diagonallimit-regular-cauchy-family-carrier} and its classifier only through the displayed $\hsame$ comparisons and $\Cont$ routes on the $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\Pkg$, and $\NameCert_{\DiagonalLimitUp}$ rows.
\end{theorem}
\begin{proof}
Project both accepted packets through \autoref{def:diagonallimit-regular-cauchy-family-carrier}. The carrier coordinates are exactly the displayed regular family, modulus, stream schedule, dyadic ledger, completion packet, real seal, package provenance, and local certificate row.

The classifier clause in the carrier definition admits only componentwise $\hsame$ comparisons and $\Cont$ read routes for those coordinates. Thus transport can rename or route a displayed row, but it cannot introduce a quotient stream, selected host limit, or ambient real object.

The precision-sensitive part of the carrier remains controlled by \autoref{thm:diagonallimit-diagonal-regularity-bound}, and the downstream route remains the handoff of \autoref{thm:diagonallimit-real-cauchy-handoff-boundary}. The exclusions in \autoref{thm:diagonallimit-non-escape-boundary} show that no further row participates in the accepted transport scope.
\end{proof}

\begin{theorem}[DiagonalLimit completion seal factorization]
\label{thm:diagonallimit-completion-seal-factorization}
Every $\RealUp$ seal read exported by an accepted $\DiagonalLimitUp$ packet factors through its $\RealDiagonalCompletionUp$ packet and the displayed $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$ readback rows selected by the packet classifier.
\end{theorem}
\begin{proof}
Start with an accepted packet and project its carrier as in \autoref{def:diagonallimit-regular-cauchy-family-carrier}. The $\RealUp$ seal coordinate is not free-standing; it is one of the visible packet rows paired with the completion packet coordinate.

Apply \autoref{thm:diagonallimit-diagonal-regularity-bound} to obtain the selected regular rational readback, stream window, and dyadic ledger for the requested precision. Then apply \autoref{thm:diagonallimit-real-cauchy-handoff-boundary}, which routes the consumer read through the same terminal precision, completion packet, seal row, $\Pkg$ provenance, and local $\NameCert_{\DiagonalLimitUp}$ row.

The non-escape boundary of \autoref{thm:diagonallimit-non-escape-boundary} rules out any alternate host-real or quotient-stream factor. Hence every seal read factors through the displayed completion packet and readback rows.
\end{proof}
\leanchecked{BEDC.Derived.DiagonalLimitUp.DiagonalLimitCarrier\_completion\_seal\_factorization}

\begin{theorem}[DiagonalLimit dependency stability package]
\label{thm:diagonallimit-dependency-stability-package}
The dependency package over $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, $\RealUp$, $\mathsf{BHist}$, $\Pkg$, and $\NameCert$ is stable under the displayed $\DiagonalLimitUp$ classifier.
\end{theorem}
\begin{proof}
The package dependencies are exactly the coordinates and provenance rows listed in \autoref{def:diagonallimit-regular-cauchy-family-carrier}. Stability therefore reduces to checking that each dependency row remains inside the same accepted packet boundary after classifier transport.

\autoref{thm:diagonallimit-obligation-transport-scope} identifies that transport boundary as the displayed $\hsame$ and $\Cont$ rows only. \autoref{thm:diagonallimit-diagonal-regularity-bound} keeps the regular-family, modulus, stream, and dyadic rows stable for every precision request.

\autoref{thm:diagonallimit-real-cauchy-handoff-boundary} keeps the completion and $\RealUp$ consumer route attached to the same provenance rows. Finally, \autoref{thm:diagonallimit-non-escape-boundary} excludes every dependency outside the named package, so the dependency package is stable under the displayed classifier.
\end{proof}

\begin{theorem}[DiagonalLimit public export]
\label{thm:diagonal-limit-public-export}
The carrier of \autoref{def:diagonallimit-regular-cauchy-family-carrier}, the NameCert surface of \autoref{thm:diagonallimit-namecert-obligation-surface}, the diagonal regularity bound of \autoref{thm:diagonallimit-diagonal-regularity-bound}, the real-Cauchy handoff boundary of \autoref{thm:diagonallimit-real-cauchy-handoff-boundary}, the non-escape boundary of \autoref{thm:diagonallimit-non-escape-boundary}, the transport scope of \autoref{thm:diagonallimit-obligation-transport-scope}, the completion seal factorization of \autoref{thm:diagonallimit-completion-seal-factorization}, and the dependency stability package of \autoref{thm:diagonallimit-dependency-stability-package} assemble the public $\DiagonalLimitUp$ export.

The export consists of the displayed regular-family rows, explicit modulus row, finite stream-window schedule, dyadic readback ledger, diagonal completion packet, $\RealUp$ seal row, componentwise transport, continuation routes, package provenance, and local naming row. It does not assert $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the finite carrier
$$
L=(F,M,S,D,C,E,P,N).
$$
The carrier and NameCert surface expose the regular-family, modulus, stream-window, dyadic-ledger, completion-packet, real-seal, package, and local naming rows.

The diagonal regularity and handoff theorems route each requested read through the displayed modulus, selected stream window, rational readback, dyadic ledger, completion packet, and seal row. The transport and dependency theorems keep those rows stable under the accepted $\hsame$ and $\Cont$ routes.

The non-escape and seal-factorization theorems exclude quotient streams, selected host limits, uniqueness of limits, host real construction, and ambient completeness. Hence the public export is the displayed finite diagonal-limit surface alone, with no claim of $\RealUp$ completeness.
\end{proof}

\closureat{DiagonalLimitUp}{seedStr}
\closureat{DiagonalLimitUp}{obligationStr}
\closureat{DiagonalLimitUp}{scopedStr}
\closureat{DiagonalLimitUp}{publicStr}
\closureat{DiagonalLimitUp}{bridgedStr}[BEDC.Derived.DiagonalLimitUp.DiagonalLimitCarrier\_completion\_seal\_factorization]
\closureat{DiagonalLimitUp}{matureStr}[BEDC.Derived.DiagonalLimitUp.DiagonalLimitCarrier\_completion\_seal\_factorization]

\begin{closurestatus}{\DiagonalLimitUp}
  \constructivestory{A $\DiagonalLimitUp$ packet is generated from a $\RegSeqRatUp$-indexed regular Cauchy family, an explicit $\CauchyModulusUp$ row, finite $\StreamNameUp$ windows, $\DyadicRatCoreUp$ observation ledgers, a $\RealDiagonalCompletionUp$ packet, a $\RealUp$ seal row, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The obligation scope registers the carrier, displayed classifier route, diagonal regularity bound, completion-to-$\RealUp$ handoff boundary, ledger non-escape surface, accepted transport scope, seal factorization, and dependency stability over $\RegSeqRatUp$, $\CauchyModulusUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, and $\RealUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.DiagonalLimitUp.DiagonalLimitCarrier\_completion\_seal\_factorization}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close $\RealUp$ completeness, quotient equality of regular streams, uniqueness of limits, host real construction, or bridge checking.}
  \upgradepath{No further theory-axis upgrade is pending; bridge checking remains a separate formal-axis obligation over the same displayed regular-family, modulus, stream-window, dyadic-ledger, completion-packet, $\RealUp$, $\Pkg$, and $\NameCert$ rows.}
\end{closurestatus}
