\chapter{A Concrete Naming Certificate for $\CompactUniformContinuityUp$}
\label{ch:concrete-instances-compactuniformcontinuity-namecert}
\origin{human}

The $\CompactUniformContinuityUp$ interface names the concrete certificate layer that realizes \autoref{thm:compact-uniform-continuity} as finite BEDC data. It sits over the same source metric as the compact and continuous-map packets: compactness contributes finite $\mathsf{ProbeBundle}$ nets from $\CompactMetricUp$, continuity contributes pointwise modulus rows from $\ContinuousMapUp$, the source and target metrics contribute $\mathsf{MetricDistanceWitness}$ rows, and the final precision is selected by positive-radius folds through $\RatUp$. The packet exports a $\NameCert$ surface for the compact-uniform-continuity handoff; it does not expose an open-cover principle, sequential compactness, a host modulus function, or a selected real-valued minimum.

\begin{definition}[CompactUniformContinuity carrier]
\label{def:compact-uniform-continuity-carrier}
A $\CompactUniformContinuityUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
H=(X,Y,F,E,D,\mathcal{P},C,M,R,W,T,Q,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $X$ is the source $\MetricUp$ row whose distance reads are witnessed by $\mathsf{MetricDistanceWitness}$;
\item $Y$ is the target $\MetricUp$ row whose distance reads are witnessed by $\mathsf{MetricDistanceWitness}$;
\item $F$ is the displayed $\ContinuousMapUp$ graph row from $X$ to $Y$;
\item $E$ is a positive $\RatUp$ tolerance history requested by the target metric consumer;
\item $D$ is the positive $\RatUp$ precision history proposed as the compact-uniform output;
\item $\mathcal{P}$ is the nonempty finite $\mathsf{ProbeBundle}$ net supplied by the $\CompactMetricUp$ packet over $X$;
\item $C$ records the compact finite-net coverage rows, including center histories and half-radius coverage witnesses for every source-point history;
\item $M$ records the $\ContinuousMapUp$ pointwise modulus rows at the bundled centers, each read through the graph row $F$ and the source and target metric ledgers;
\item $R$ records the positive-radius $\RatUp$ rows and comparison rows used by the fold, including the half-radius histories consumed by the finite cover;
\item $W$ is the finite lower-bound fold witness proving that $D$ is classifier-stably below every bundled half-radius row;
\item $T$ records the componentwise $\hsame$ rows for source metrics, target metrics, graph rows, tolerance rows, precision rows, finite-net rows, pointwise-modulus rows, radius rows, and fold rows;
\item $Q$ records the displayed $\Cont$ routes by which compact, continuous-map, metric, rational-fold, and compact-uniform-continuity consumers read the packet;
\item $P$ is the $\Pkg$ provenance row over $\MetricUp$, $\CompactMetricUp$, $\ContinuousMapUp$, $\RatUp$, and the closed $\mathsf{ProbeBundle}$ spine;
\item $N$ is the local $\NameCert_{\CompactUniformContinuityUp}$ row.
\end{enumerate}
The carrier contains only the displayed finite-net, pointwise-modulus, metric-distance, positive-rational, transport, continuation, package, and naming rows. It contains no hidden point selector, no quotient of source histories, no ambient minimum operator, and no analytic compactness theorem beyond the finite packet.
\end{definition}

\begin{definition}[CompactUniformContinuity classifier]
\label{def:compact-uniform-continuity-classifier}
For accepted $\CompactUniformContinuityUp$ carriers $H$ and $H'$, the classifier $\mathsf{CompactUniformContinuityClassifier}(H,H')$ compares exactly the visible rows of \autoref{def:compact-uniform-continuity-carrier}. Source and target metric rows compare through their displayed $\hsame$ and $\Cont$ routes; compact finite-net rows compare through the same $\mathsf{ProbeBundle}$ spine and coverage witnesses; continuous-map rows compare through the pointwise modulus ledger; positive tolerance, precision, radius, and fold rows compare through the $\RatUp$ classifier; and the package and local naming rows compare through their displayed $\Pkg$ and $\NameCert$ provenance.

The classifier does not compare external functions, open covers, sequences, host real endpoints, selected minima, or unrecorded continuity data.
\end{definition}

\begin{theorem}[CompactUniformContinuity NameCert obligations]
\label{thm:compact-uniform-continuity-namecert-obligations}
The local $\NameCert_{\CompactUniformContinuityUp}$ obligation surface consists of carrier habitation, displayed classifier transport, compact finite-net coverage over $\CompactMetricUp$ and $\mathsf{ProbeBundle}$, continuous pointwise-modulus handoff over $\ContinuousMapUp$, metric-distance routing through $\mathsf{MetricDistanceWitness}$, positive-radius lower-bound folding over $\RatUp$, and downstream non-escape through the recorded $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows.
\end{theorem}
\leanchecked{BEDC.Derived.CompactUniformContinuityUp.CompactUniformContinuityPacket\_namecert\_obligations}
\begin{proof}
Carrier habitation is the finite packet of \autoref{def:compact-uniform-continuity-carrier}. Every row named by the compact-uniform certificate has a visible coordinate before any consumer can read it.

Classifier transport is componentwise by \autoref{def:compact-uniform-continuity-classifier}. The compact rows transport finite-net coverage, the continuous rows transport pointwise modulus data, the metric rows transport distance witnesses, and the rational rows transport positive-radius comparisons and the lower-bound fold.

The obligation surface is therefore exactly the displayed handoff from compact finite nets and pointwise continuity to a uniform precision history. Repacking those rows with $T$, $Q$, $P$, and $N$ gives the local $\NameCert_{\CompactUniformContinuityUp}$ surface, while external selectors, sequence principles, open-cover compactness, and hidden minima remain outside the carrier.
\end{proof}

\begin{theorem}[CompactUniformContinuity finite-net handoff]
\label{thm:compact-uniform-continuity-finite-net-handoff}
Suppose an accepted $\CompactUniformContinuityUp$ carrier has tolerance history $E$, precision history $D$, compact finite-net spine $\mathcal{P}$, coverage rows $C$, pointwise-modulus rows $M$, positive-radius rows $R$, and lower-bound fold witness $W$. Then every source-distance read below $D$ factors through one bundled center in $\mathcal{P}$, the corresponding $\mathsf{MetricDistanceWitness}$ rows in $X$, the corresponding pointwise-modulus row in $M$, and the target metric rows in $Y$. The result is the uniform-modulus ledger promised by \autoref{thm:compact-uniform-continuity}, read as finite $\NameCert_{\CompactUniformContinuityUp}$ data.
\end{theorem}
\begin{proof}
Read the compact coordinate first. The $\CompactMetricUp$ row supplies the nonempty $\mathsf{ProbeBundle}$, center histories, half-radius histories, and coverage rows saying that each source-point history is covered by some bundled center.

Read the rational fold next. The witness $W$ records a primitive finite fold over the positive-radius rows $R$, so the selected precision history $D$ compares below every bundled half-radius through the $\RatUp$ classifier and the transported $\hsame$ rows.

Given two source histories whose displayed distance is below $D$, the coverage row chooses the bundled center for the first history. The fold comparison and the source metric triangle row route the second history into the same local ball, with all distances witnessed by $\mathsf{MetricDistanceWitness}$.

Finally use the $\ContinuousMapUp$ pointwise-modulus row attached to that bundled center and the target metric triangle row. Both source histories are inside the same displayed pointwise ball, so the two target histories are within the requested tolerance row $E$. All reads pass through the carrier coordinates, hence the handoff is a $\NameCert_{\CompactUniformContinuityUp}$ row rather than an external Heine--Cantor theorem.
\end{proof}

\begin{theorem}[CompactUniformContinuity radius-fold exactness]
\label{thm:compact-uniform-continuity-radius-fold-exactness}
In every accepted $\CompactUniformContinuityUp$ carrier
$H=(X,Y,F,E,D,\mathcal{P},C,M,R,W,T,Q,P,N)$, the precision row $D$ is accepted
by the classifier exactly as the finite lower-bound fold over the
positive-radius ledger $R$. Every compact finite-net center in
$\mathcal{P}$ receives a displayed half-radius comparison below $D$, and
classifier transport through $T$, $Q$, $P$, and $N$ preserves that fold
surface.

Consequently the uniform precision consumed by the finite-net handoff is the
displayed rational fold output, not a hidden point selector, selected real
minimum, open-cover compactness principle, sequential compactness principle,
or external modulus function.
\end{theorem}
\begin{proof}
Project the positive-radius ledger $R$ and the fold witness $W$ from the
carrier. The witness records a finite $\RatUp$ lower-bound fold whose output
is the displayed precision row $D$.

For each center in the finite $\mathsf{ProbeBundle}$ spine $\mathcal{P}$, the
same ledger supplies the positive radius used by the pointwise-modulus row,
and $W$ supplies the comparison placing $D$ below the corresponding
half-radius history.

The classifier is componentwise on $T$, routed by $Q$, and packaged by $P$ and
$N$. Thus transport can carry the $\RatUp$ comparisons and the fold row across
classified carriers, but it cannot introduce a new minimum operation or an
unrecorded radius source.

Feeding these transported comparisons into
\autoref{thm:compact-uniform-continuity-finite-net-handoff} gives the same
uniform-modulus ledger for every accepted representative. The handoff reads
finite rational fold data rather than external compactness or host real
selection data.
\end{proof}

\begin{theorem}[CompactUniformContinuity real-seal boundary]
\label{thm:compact-uniform-continuity-real-seal-boundary}
When the source and target metrics are consumed through $\RealUp$ or interval-shaped $\RealUp$ packets, an accepted $\CompactUniformContinuityUp$ carrier can expose only the finite-net coverage rows, $\mathsf{MetricDistanceWitness}$ rows, pointwise-modulus rows, positive $\RatUp$ fold rows, and the resulting uniform precision history. It cannot expose host real equality, a selected real minimum, sequential compactness, open-cover compactness, or an external modulus function at the real-seal boundary.
\end{theorem}
\begin{proof}
Project the carrier through its metric coordinates $X$ and $Y$. A real-valued consumer reaches those coordinates only through displayed metric rows and their $\mathsf{MetricDistanceWitness}$ evidence.

The compact information available at the boundary is the finite $\mathsf{ProbeBundle}$ ledger $C$. The continuous information available there is the pointwise-modulus ledger $M$. The positive lower bound available there is the $\RatUp$ fold row $W$ over the radius ledger $R$.

Since these rows exhaust the carrier coordinates exposed to real-name consumers, the seal can export only the resulting finite uniform-precision packet. Host real equality, selected minima, sequence arguments, open covers, and external modulus functions have no coordinate from which they could be read.
\end{proof}

\begin{theorem}[CompactUniformContinuity ProbeBundle coverage]
\label{thm:compact-uniform-continuity-probebundle-coverage}
In every accepted $\CompactUniformContinuityUp$ carrier
$H=(X,Y,F,E,D,\mathcal{P},C,M,R,W,T,Q,P,N)$, every source-point read used by the compact-uniform-continuity handoff factors through the finite $\mathsf{ProbeBundle}$ spine $\mathcal{P}$, one displayed center history in $C$, the associated half-radius coverage row, and the same transported $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows that classify $H$.
\end{theorem}
\begin{proof}
Project the carrier by \autoref{def:compact-uniform-continuity-carrier}. The finite net coordinate $\mathcal{P}$ and the coverage ledger $C$ are visible before the continuous-map and rational-fold rows are consumed.

The classifier of \autoref{def:compact-uniform-continuity-classifier} transports these rows componentwise. Thus a classified replacement of the carrier preserves the same bundled center histories, the same half-radius coverage witnesses, and the same continuation routes by which a source-point read reaches them.

The local obligation statement in \autoref{thm:compact-uniform-continuity-namecert-obligations} identifies this coverage as part of the $\NameCert_{\CompactUniformContinuityUp}$ surface. Feeding the selected bundled center into \autoref{thm:compact-uniform-continuity-finite-net-handoff} gives the uniform-precision route, and \autoref{thm:compact-uniform-continuity-real-seal-boundary} confirms that no open-cover or sequence principle is exported in place of the finite $\mathsf{ProbeBundle}$ ledger.
\end{proof}

\begin{theorem}[CompactUniformContinuity metric-distance routing]
\label{thm:compact-uniform-continuity-metric-distance-routing}
For every accepted $\CompactUniformContinuityUp$ carrier, each source metric read used to enter a bundled center ball and each target metric read used to compare output histories is routed through a displayed $\mathsf{MetricDistanceWitness}$ row in the source or target metric coordinate. No source or target distance is read directly from a host metric function outside the carrier.
\end{theorem}
\begin{proof}
The carrier of \autoref{def:compact-uniform-continuity-carrier} names the source metric row $X$ and target metric row $Y$ as the only metric coordinates. Both are read through displayed $\mathsf{MetricDistanceWitness}$ evidence and transported with the componentwise rows $T$ and routes $Q$.

By \autoref{def:compact-uniform-continuity-classifier}, classified carriers compare metric rows only through those displayed witnesses. Hence a source-distance comparison below $D$, a half-radius comparison around a bundled center, and a target-distance comparison below $E$ all remain inside the same metric-distance ledgers.

The finite-net route of \autoref{thm:compact-uniform-continuity-finite-net-handoff} uses exactly these source and target reads, while \autoref{thm:compact-uniform-continuity-namecert-obligations} records metric-distance routing as a local naming obligation. The boundary statement in \autoref{thm:compact-uniform-continuity-real-seal-boundary} then prevents a real-name consumer from replacing those witnesses by host metric access.
\end{proof}

\begin{theorem}[CompactUniformContinuity non-escape ledger]
\label{thm:compact-uniform-continuity-non-escape-ledger}
An accepted $\CompactUniformContinuityUp$ packet exports only the finite $\mathsf{ProbeBundle}$ coverage rows, $\mathsf{MetricDistanceWitness}$ rows, pointwise-modulus rows, positive $\RatUp$ fold rows, displayed transports, continuation routes, package provenance, and local naming provenance. It exports no open-cover compactness principle, no sequential compactness principle, no host minimum, and no external modulus function.
\end{theorem}
\begin{proof}
Inspect the carrier in \autoref{def:compact-uniform-continuity-carrier}. Its coordinates list the compact finite-net data, continuous pointwise-modulus rows, source and target metric witnesses, rational-radius fold data, transports, routes, package row, and local certificate row.

The classifier in \autoref{def:compact-uniform-continuity-classifier} compares exactly those coordinates. It has no component for open covers, sequences, host minima, or unrecorded modulus functions, so those objects cannot be introduced by classifier transport.

The obligation surface of \autoref{thm:compact-uniform-continuity-namecert-obligations} and the handoff of \autoref{thm:compact-uniform-continuity-finite-net-handoff} use the same finite rows to produce the uniform precision history. Finally, \autoref{thm:compact-uniform-continuity-real-seal-boundary} states the real-seal boundary for these rows, so the exported packet remains a finite BEDC ledger and not a classical Heine--Cantor artifact.
\end{proof}

\begin{theorem}[CompactUniformContinuity modulus choice surface]
\label{thm:compact-uniform-continuity-modulus-choice-surface}
For every accepted $\CompactUniformContinuityUp$ packet, the uniform precision row consumed by the compact-uniform-continuity handoff is determined only by the finite $\mathsf{ProbeBundle}$ centers, the $\ContinuousMapUp$ pointwise-modulus rows attached to those centers, the positive $\RatUp$ radius ledger, and the finite lower-bound fold witness. It is not determined by an open cover, a sequential compactness argument, a selected real minimum, or a host modulus function.
\end{theorem}
\begin{proof}
Project the packet through the carrier in \autoref{def:compact-uniform-continuity-carrier}. The only coordinates from which a precision row can be read are the finite $\mathsf{ProbeBundle}$ spine, the centerwise modulus ledger, the positive-radius ledger, and the fold witness.

The classifier in \autoref{def:compact-uniform-continuity-classifier} preserves those rows componentwise. The finite-net handoff of \autoref{thm:compact-uniform-continuity-finite-net-handoff} and the radius-fold exactness statement of \autoref{thm:compact-uniform-continuity-radius-fold-exactness} then identify the consumed precision row with the displayed lower-bound fold output.

Finally, \autoref{thm:compact-uniform-continuity-probebundle-coverage}, \autoref{thm:compact-uniform-continuity-metric-distance-routing}, and \autoref{thm:compact-uniform-continuity-non-escape-ledger} rule out any route through unrecorded compactness, host minima, or external modulus selection.
\end{proof}

\begin{theorem}[CompactUniformContinuity center-radius compatibility]
\label{thm:compact-uniform-continuity-center-radius-compatibility}
In every accepted $\CompactUniformContinuityUp$ carrier, each bundled center in the finite $\mathsf{ProbeBundle}$ spine has a compatible half-radius row in the positive $\RatUp$ ledger. The source metric reads that place histories inside that half-radius ball and the target metric reads that consume the corresponding pointwise modulus are mediated by displayed $\mathsf{MetricDistanceWitness}$ rows.
\end{theorem}
\begin{proof}
Read the finite-net coordinate and coverage ledger from \autoref{def:compact-uniform-continuity-carrier}. Each center history appears with the half-radius coverage row supplied by the compact packet and with the positive-radius data recorded in $R$.

The radius-fold exactness theorem \autoref{thm:compact-uniform-continuity-radius-fold-exactness} supplies the comparison between the displayed precision row and every bundled half-radius. The ProbeBundle coverage theorem \autoref{thm:compact-uniform-continuity-probebundle-coverage} keeps the same center and half-radius rows under classifier transport.

Metric access is then fixed by \autoref{thm:compact-uniform-continuity-metric-distance-routing}. Source reads into the center ball and target reads from the pointwise-modulus conclusion both pass through $\mathsf{MetricDistanceWitness}$ rows, and the non-escape ledger of \autoref{thm:compact-uniform-continuity-non-escape-ledger} leaves no direct host-metric read outside those witnesses.
\end{proof}

\begin{theorem}[CompactUniformContinuity uniform precision consumer route]
\label{thm:compact-uniform-continuity-uniform-precision-consumer-route}
For an accepted $\CompactUniformContinuityUp$ packet, any consumer read below the displayed precision factors through compact finite coverage, one bundled center row, the center's $\ContinuousMapUp$ modulus row, source and target $\mathsf{MetricDistanceWitness}$ rows, the transported $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and the local $\NameCert_{\CompactUniformContinuityUp}$ row. The route contains no open-cover compactness, sequential compactness, selected real minimum, or host modulus.
\end{theorem}
\begin{proof}
Begin with the carrier and classifier. By \autoref{def:compact-uniform-continuity-carrier} the consumer can read only the displayed compact, continuous-map, metric, rational, transport, route, package, and naming coordinates, and by \autoref{def:compact-uniform-continuity-classifier} those coordinates are the complete comparison surface.

The finite-net handoff in \autoref{thm:compact-uniform-continuity-finite-net-handoff} routes a read below the displayed precision through a covered center. The radius-fold exactness statement \autoref{thm:compact-uniform-continuity-radius-fold-exactness} supplies the half-radius comparison needed to enter the center row, and \autoref{thm:compact-uniform-continuity-center-radius-compatibility} identifies the compatible metric witnesses used there.

At the center, the pointwise-modulus row from $\ContinuousMapUp$ produces the target tolerance read. The ProbeBundle coverage theorem, metric-distance routing theorem, modulus choice surface, and non-escape ledger then show that the whole consumer route is carried by $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ provenance rather than by open covers, sequences, host minima, or an external modulus.
\end{proof}

\closureat{CompactUniformContinuityUp}{seedStr}
\closureat{CompactUniformContinuityUp}{obligationStr}
\closureat{CompactUniformContinuityUp}{scopedStr}
\closureat{CompactUniformContinuityUp}{publicStr}

\begin{closurestatus}{\CompactUniformContinuityUp}
  \constructivestory{A $\CompactUniformContinuityUp$ packet is generated from source and target metric rows, a continuous-map graph row, a positive tolerance history, a compact finite $\mathsf{ProbeBundle}$ net, pointwise-modulus rows at the bundled centers, positive $\RatUp$ radius rows, a finite lower-bound fold selecting a precision history, componentwise $\hsame$ rows, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\publicClosure}
  \scopeclosed{The scoped dependency surface is fixed by the carrier, classifier, finite-net handoff, radius-fold exactness, $\mathsf{ProbeBundle}$ coverage, metric-distance routing, non-escape ledger, modulus-choice surface, center-radius compatibility, and uniform-precision consumer route.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close a checked Lean implementation, bridge status, open-cover compactness, sequential compactness, host real equality, selected real minima, or external modulus selection.}
  \upgradepath{The next paper grade is bridged closure by supplying the bridge theorem from this public compact-uniform-continuity interface to the standard compact-metric uniform-continuity reading.}
\end{closurestatus}
