\begin{theorem}[Rat representative classifier stability package]
\label{thm:rat-representative-classifier-stability-package}
Fix a rational source normalizer
$\mathsf{normalized}:\mathsf{BMark}\to\mathsf{BHist}\to\mathsf{BHist}\to\mathsf{Prop}$.
For every representative triple $s,n,d$ with
$\mathsf{RatSourceSpec}(\mathsf{normalized},s,n,d)$, the row
$\mathsf{RatSourceSpec\_to\_RatCarrier}$ supplies the representative carrier
$\mathsf{RatCarrier}(s,n,d)$.

On such representatives the classifier
$\mathsf{RatClassifierSpec}$ is stable in the following sense:
\begin{enumerate}
\item $\mathsf{RatClassifierSpec}$ is reflexive on every representative
carrier.
\item $\mathsf{RatClassifierSpec}$ is symmetric on classified representative
pairs.
\item $\mathsf{RatClassifierSpec}$ is transitive along composable
representative pairs.
\item If signs are related by $\msame$ and numerator and denominator histories
are related by $\hsame$, then each classified representative pair transports
componentwise to the displayed representatives.
\end{enumerate}
Thus the representative classifier used by the $\RatUp$ name certificate is
an equivalence relation on normalized representatives and is stable under
the BEDC component sameness relations for signs, numerators, and denominators.
\end{theorem}
\begin{proof}
Start with a representative source witness
$\mathsf{RatSourceSpec}(\mathsf{normalized},s,n,d)$. The checked row
$\mathsf{RatSourceSpec\_to\_RatCarrier}$ converts it into the carrier witness
needed by the representative classifier.

The equivalence portion is supplied by three checked rows. Apply
$\mathsf{RatClassifierSpec\_refl}$ to a representative carrier for
reflexivity, apply $\mathsf{RatClassifierSpec\_symm}$ to reverse any classified
representative pair, and apply $\mathsf{RatClassifierSpec\_trans}$ to compose
two adjacent classified representative pairs.

For component stability, use
$\mathsf{RatClassifierSpec\_component\_transport}$. Its hypotheses are exactly
the displayed $\msame$ links on the two signs and the displayed $\hsame$ links
on the two numerator histories and the two denominator histories, so it moves
the classifier edge to the transported representative data.

The statement therefore packages the representative carrier conversion, the
three equivalence laws, and component transport as one certificate layer. It
records the combined representative-level stability supplied by several
checked rows rather than restating any single row.
\end{proof}
