\chapter{A Concrete Naming Certificate for \(\RatUp\)}
\label{ch:concrete-instances-rat-namecert}

The rational number interface $\RatUp$ starts from a carrier skeleton: a signed unary integer numerator, drawn from \autoref{ch:concrete-instances-int-namecert}, together with a positive unary denominator. Normalized representatives, coprimality, and arithmetic closure are separate source, pattern, classifier, and stability obligations later in the chapter. The classifier is structural equality on the normalized representative, not the equivalence relation $p_1 q_2 = p_2 q_1$ on unnormalized pairs, which would otherwise demand quotient-type machinery and $\mathsf{Quot.sound}$. It is not a primitive field; it is licensed only via the integer source and the normalization function.

\begin{remark}[Rational certificate scope]
\label{rem:concrete-instances-rat-namecert-roadmap}
This chapter records the rational licensing target through normalized
integer-positive-natural representatives and structural classifier data.
The checked core covers the rational history carrier, rational history classifier fields, ledger carrier, and semantic certificate. Normalized representatives are recorded by the source and pattern obligations, while coprimality and operation closure remain part of the paper specification.
\end{remark}

\section{Carrier definition}

\begin{definition}[Rat carrier]
\label{def:rat-carrier}
Use only the carrier skeleton: a signed unary integer numerator together with a unary denominator history that is not internally the same as $\emp$:
$$
  \mathsf{RatCarrier}(s,n,d)
  :=
  \mathsf{IntCarrier}(s,n)\land \mathsf{Unary}(d)\land \neg\hsame(d,\emp).
$$
Equivalently, this is an $\IntUp$ numerator with a positive unary-history denominator. At this skeleton layer, positivity is witnessed by writing the denominator as a one-extension of a unary tail; normalized representatives, coprimality, and arithmetic closure are supplied by later source, pattern, and stability obligations.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatCarrier}

\begin{theorem}[Rat carrier positive denominator]
\label{thm:rat-carrier-positive-denominator}
If \(\mathsf{RatCarrier}(s,n,d)\), then the denominator is internally the same as \(\Eone(t)\) for some unary tail \(t\).
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_positive\_denominator}
\begin{proof}
Unpack the carrier into its integer numerator, unary denominator, and non-emptiness clauses. The unary denominator is either \(\emp\) or a one-extension of a unary tail. The empty case contradicts non-emptiness, while the one-extension case gives the displayed positive-denominator witness.
\end{proof}

\begin{theorem}[Positive denominator yields a rational carrier]
\label{thm:rat-carrier-from-positive-denominator}
An \(\IntUp\) numerator together with a denominator internally same as
\(\Eone(t)\) for a unary tail \(t\) forms a \(\RatUp\) carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_of\_int\_positive\_denominator}
\begin{proof}
Transport unary closure from the displayed \(\Eone\)-shape to the denominator
along \(\hsame\). Non-emptiness follows because an \(\Eone\)-history cannot be
internally same as \(\emp\).
\end{proof}

\begin{theorem}[Rat carrier denominator transport]
\label{thm:rat-carrier-denominator-hsame-transport}
If \(\mathsf{RatCarrier}(s,n,d)\) and \(d\hsame d'\), then
\(\mathsf{RatCarrier}(s,n,d')\).
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_denominator\_hsame\_transport}
\begin{proof}
Extract the positive denominator witness from the rational carrier, transport
that witness across denominator sameness, and rebuild the rational carrier from
the unchanged integer numerator together with the transported positive
denominator.
\end{proof}

\begin{theorem}[Positive unary denominator transport]
\label{thm:rat-positive-unary-denominator-hsame-transport}
If a denominator history has a positive unary witness and is \(\hsame\)-equivalent to another history, then the other history has the same positive unary denominator witness.
\end{theorem}
\begin{proof}
Write the positive denominator as an \(\Eone\)-extension of a unary tail. Compose the reverse \(\hsame\) witness from the target history to the source history with the source witness to the \(\Eone\)-extension, and keep the unary tail witness.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_hsame\_transport}

\begin{theorem}[One-extension positive denominator equivalence]
\label{thm:rat-positive-unary-denominator-eone-iff-unary}
A one-extension history has a positive unary denominator witness exactly when
its tail is unary.
\end{theorem}
\begin{proof}
For the forward direction, eliminate the positive-denominator witness
\(\hsame(\Eone(t),\Eone(u))\) with unary tail \(u\). One-constructor inversion
gives \(\hsame(t,u)\), and unary membership transports back to \(t\). For the
reverse direction, use \(t\) itself as the displayed positive tail and the
reflexive one-extension sameness witness.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_e1\_iff\_unary}

\begin{theorem}[Zero-extension cannot be a positive denominator]
\label{thm:rat-positive-denominator-e0-absurd}
A zero-extension history has no positive unary denominator witness.
\end{theorem}
\begin{proof}
Unpack the positive denominator witness. It would identify an
\(\Ezero\)-history with an \(\Eone\)-history, contradicting finite-kernel
history constructor no-confusion.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_e0\_absurd}

\begin{theorem}[Positive unary denominator is not empty]
\label{thm:rat-positive-unary-denominator-not-empty}
If a denominator has a positive unary witness, then it is not internally the
same as \(\emp\).
\end{theorem}
\begin{proof}
Unpack the positive denominator as internally the same as \(\Eone(t)\) for a
unary tail \(t\). Composing this witness with an assumed sameness to \(\emp\)
would make an \(\Eone\)-history internally the same as \(\emp\), contradicting
history constructor no-confusion.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_not\_empty}

\begin{theorem}[Positive unary denominator is unary and nonempty]
\label{thm:positive-unary-denominator-unary-and-nonempty}
If a denominator history has a positive unary witness, then it is unary and cannot be internally the same as \(\emp\).
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_unary\_and\_nonempty}
\begin{proof}
Write the positive denominator as internally the same as \(\Eone(t)\) with \(t\) unary. Unary closure under \(\Eone\), transported back along history sameness, gives unary membership of the denominator. If the denominator were internally same as \(\emp\), transitivity would make \(\Eone(t)\) internally same as \(\emp\), contradicting constructor separation.
\end{proof}

\begin{theorem}[Positive unary denominator carrier equivalence]
\label{thm:rat-carrier-iff-positive-unary-denominator}
The rational carrier condition is equivalent to an $\IntUp$ numerator together with a denominator that has a positive unary tail witness.
\end{theorem}
\begin{proof}
Unpack the carrier. A unary denominator that is not $\hsame$-empty cannot be the empty unary history, so unary case analysis gives a one-extension tail. Conversely, a denominator $\hsame$-equal to a one-extension of a unary tail is unary by transport, and it cannot be $\hsame$-empty by constructor no-confusion.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_iff\_positive\_unary\_denominator}

\begin{theorem}[Positive denominator append unary tail]
\label{thm:rat-positive-denominator-append-unary-tail}
If a denominator has a positive unary witness and the appended tail is unary, then the continued denominator still has a positive unary witness.
\end{theorem}
\begin{proof}
Write the denominator as internally the same as \(\Eone(t)\) for a unary tail \(t\), and transport unary membership back to the denominator itself. The appended tail is either \(\emp\) or a one-step unary tail. The empty case keeps the original witness, while the one-step case takes the continued denominator without that final step as the new positive tail; closure follows from unary append closure.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_append\_unary\_tail}

\begin{theorem}[Rat carrier append unary denominator closure]
\label{thm:rat-carrier-append-unary-denominator-closed}
If a rational carrier has denominator \(d\), then appending any unary history to
\(d\) preserves rational-carrier membership.
\end{theorem}
\begin{proof}
Use the carrier equivalence to expose the integer numerator carrier and the
positive unary denominator witness. Positive denominators are closed under
appending unary tails, and the rational carrier is rebuilt from the same
integer numerator and the resulting positive denominator.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_append\_unary\_denominator\_closed}

\begin{theorem}[Rat history carrier is not empty]
\label{thm:rat-history-carrier-not-empty}
If a rational history carrier has denominator \(d\), then \(d\) cannot be
internally the same as \(\emp\).
\end{theorem}
\begin{proof}
Unpack the rational history carrier into its sign, numerator, and rational
carrier. The rational carrier exposes a positive unary denominator witness, and
positive unary denominators are separated from \(\emp\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_not\_empty}

\begin{theorem}[Rat history carrier positive denominator equivalence]
\label{thm:rat-history-carrier-positive-denominator-equivalence}
A denominator history lies in the rational history carrier exactly when it has
a positive unary denominator witness.
\end{theorem}
\begin{proof}
In the forward direction, unpack the rational history carrier into a sign,
numerator, and rational carrier, then apply rational-carrier positivity of the
denominator. In the reverse direction, use the concrete integer numerator
carrier with sign $\bzero$ and empty magnitude, then rebuild the rational
carrier from the positive denominator witness.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_iff\_positive\_denominator}

\begin{theorem}[Rat history eone tail unary equivalence]
\label{thm:rat-history-carrier-e1-tail-unary-iff}
A one-extension denominator \(\Eone(t)\) lies in the rational history carrier
exactly when its tail \(t\) is unary.
\end{theorem}
\begin{proof}
For the forward direction, unpack the rational history carrier to obtain the
positive denominator witness, then invert the displayed one-extension
denominator to transport unary membership to \(t\). For the reverse direction,
use the canonical integer numerator with sign \(\bzero\) and empty magnitude,
and use \(t\) itself as the positive unary denominator tail.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_e1\_tail\_unary\_iff}

\begin{theorem}[Rat history carrier excludes zero-extension]
\label{thm:rat-history-carrier-e0-absurd}
No zero-extension history \(\Ezero(t)\) lies in the rational history carrier.
\end{theorem}
\begin{proof}
Unpack the rational history carrier into its sign, numerator, and rational
carrier. The rational carrier supplies a positive unary denominator witness,
and positive unary denominators cannot have zero-extension shape.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_e0\_absurd}

\begin{theorem}[Rat history carrier append unary denominator closure]
\label{thm:rat-history-carrier-append-unary-denominator-closed}
If a rational history carrier has denominator \(d\), then appending any unary history to \(d\) preserves rational history carrier membership.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_append\_unary\_denominator\_closed}
\begin{proof}
Unpack the rational history carrier into its sign, numerator, and rational carrier data. Apply rational-carrier denominator append closure to the concrete denominator component, then rebuild the existential rational history carrier with the same sign and numerator.
\end{proof}

\begin{theorem}[Positive denominator append unary prefix]
\label{thm:rat-positive-denominator-append-unary-prefix}
If $u$ is unary and $d$ has a positive unary denominator witness, then
$\mathsf{append}(u,d)$ has a positive unary denominator witness.
\end{theorem}
\begin{proof}
Write the positive denominator witness as an $\Eone$ tail, say $d$ is
internally the same as $\Eone(t)$ with $t$ unary. Appending the unary prefix
$u$ preserves unary structure by unary append closure, and composing the
displayed $\Eone$ witness with append compatibility gives the required
positive witness for $\mathsf{append}(u,d)$.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_append\_unary\_prefix}

\begin{theorem}[Positive denominator append unary context]
\label{thm:rat-positive-denominator-append-unary-context}
If $p$ and $t$ are unary histories and $d$ has a positive unary denominator
witness, then $\mathsf{append}(p,\mathsf{append}(d,t))$ has a positive unary
denominator witness.
\end{theorem}
\begin{proof}
First close the positive denominator under the unary tail $t$. Then close the
resulting positive denominator under the unary prefix $p$.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.PositiveUnaryDenominator\_append\_unary\_context}

\begin{theorem}[Rat carrier prepend unary denominator closure]
\label{thm:rat-carrier-prepend-unary-denominator-closed}
If a rational carrier has denominator \(d\), then prepending any unary history
to \(d\) preserves rational-carrier membership.
\end{theorem}
\begin{proof}
Use the carrier equivalence to expose the integer numerator carrier and the
positive unary denominator witness. Positive denominators are closed under
unary prefix continuation, and the rational carrier is rebuilt from the same
integer numerator and the resulting positive denominator.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_prepend\_unary\_denominator\_closed}

\begin{theorem}[Rat history carrier prepend unary denominator closure]
\label{thm:rat-history-carrier-prepend-unary-denominator-closed}
If a rational history carrier has denominator \(d\), then prepending any unary
history to \(d\) preserves rational history carrier membership.
\end{theorem}
\begin{proof}
Unpack the rational history carrier into its sign, numerator, and rational
carrier data. Apply rational-carrier denominator prepend closure to the
concrete denominator component, then rebuild the existential rational history
carrier with the same sign and numerator.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_prepend\_unary\_denominator\_closed}

\begin{theorem}[Rat carrier unary denominator context closure]
\label{thm:rat-carrier-unary-denominator-context-closed}
If a rational carrier has denominator \(d\), then placing a unary prefix and a
unary tail around \(d\) preserves rational-carrier membership.
\end{theorem}
\begin{proof}
First close the carrier under appending the unary tail to the denominator.
Then close the resulting carrier under prepending the unary prefix to that
continued denominator.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_unary\_denominator\_context\_closed}

\begin{theorem}[Rat history carrier unary denominator context closure]
\label{thm:rat-history-carrier-unary-denominator-context-closed}
If a rational history carrier has denominator \(d\), then placing a unary
prefix and a unary tail around \(d\) preserves rational history carrier
membership.
\end{theorem}
\begin{proof}
Unpack the rational history carrier into its sign, numerator, and rational
carrier data. Apply rational-carrier unary denominator context closure to the
concrete denominator component, then rebuild the existential rational history
carrier with the same sign and numerator.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryCarrier\_unary\_denominator\_context\_closed}

\begin{theorem}[Rat carrier hsame transport]
\label{thm:rat-carrier-hsame-transport}
If a rational carrier \(\mathsf{RatCarrier}(s,n,d)\) is transported along
\(\msame(s,t)\), \(\hsame(n,n')\), and \(\hsame(d,d')\), then the transported
triple is again a rational carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatCarrier\_hsame\_transport}
\begin{proof}
Eliminate the sign sameness, then unpack the rational carrier. The numerator
is transported by the integer carrier transport theorem, denominator unary
closure is transported along \(\hsame(d,d')\), and denominator non-emptiness is
preserved by composing \(\hsame(d,d')\) with any empty-target witness.
\end{proof}

\section{The certificate}

\begin{definition}[Rat source specification]
\label{def:rat-source-specification}
The source is \(\IntUp \times \NatUp\) restricted to normalized denominator-positive pairs.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatSourceSpec}

\begin{theorem}[Rat source specification yields the carrier]
\label{thm:rat-source-spec-to-carrier}
A rational source witness determines a rational carrier witness: the numerator
is an integer carrier, the denominator is unary, and the positive one-tail
witness excludes internal sameness with \(\emp\).
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatSourceSpec\_to\_RatCarrier}
\begin{proof}
Unpack the source witness. The positive-denominator component gives a unary
tail \(t\) with \(d \hsame e_1(t)\). Unary closure under one-extension and
transport along \(\hsame\) give \(\mathsf{Unary}(d)\). If \(d\hsame \emp\),
then symmetry and transitivity give \(e_1(t)\hsame \emp\), contradicting
finite-kernel history no-confusion.
\end{proof}

\begin{definition}[Rat pattern specification]
\label{def:rat-pattern-specification}
The pattern is normalized numerator/denominator construction via a total normalization function on integer and positive-natural inputs.
\end{definition}

\begin{definition}[Rat classifier specification]
\label{def:rat-classifier-specification}
The classifier is structural sameness of normalized numerator and denominator representatives, tracked by mark sameness on signs and history sameness on the numerator and denominator histories.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatClassifierSpec}

\begin{theorem}[Rat classifier reflexivity]
\label{thm:rat-classifier-reflexivity}
Every rational carrier witness classifies its representative with itself.
\end{theorem}
\begin{proof}
Reuse the carrier witness for both endpoints. The sign component is witnessed by reflexivity of \(\msame\), and the numerator and denominator components are witnessed by reflexivity of \(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_refl}

\begin{theorem}[Rat classifier exposes positive denominators]
\label{thm:rat-classifier-positive-denominators}
If two rational representatives are related by the rational classifier, then
both endpoint denominators carry positive unary denominator witnesses.
\end{theorem}
\begin{proof}
Eliminate the classifier witness to expose the two endpoint rational carriers.
Apply the rational-carrier positive-denominator theorem to each endpoint
carrier.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_positive\_denominators}

\begin{theorem}[Rat classifier transports positive denominators]
\label{thm:rat-classifier-denominator-positive-transport}
If two rational representatives are related by the rational classifier, and
each denominator is related by \(\hsame\) to a displayed denominator history,
then both displayed denominator histories carry positive unary denominator
witnesses.
\end{theorem}
\begin{proof}
Eliminate the classifier witness to expose the two endpoint rational carriers.
Each endpoint carrier gives a positive unary denominator witness, and the two
denominator \(\hsame\) links transport those witnesses to the displayed
denominator histories.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_denominator\_positive\_transport}

\begin{theorem}[Rat classifier denominator append closure]
\label{thm:rat-classifier-append-unary-denominators-closed}
If two rational representatives are classified the same, then appending
\(\hsame\)-matching unary histories to their denominators preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
Unpack the classifier witness into the two endpoint carriers and the sign,
numerator, and denominator sameness fields. Close both endpoint denominator
carriers under unary append, transporting the unary-tail witness along the
tail sameness for the second endpoint. The resulting denominator sameness follows by
eliminating the original denominator and tail sameness witnesses and applying
reflexivity to the resulting append history.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_append\_unary\_denominators\_closed}

\begin{theorem}[Rat classifier denominator prepend closure]
\label{thm:rat-classifier-prepend-unary-denominators-closed}
If two rational representatives are classified the same, then prepending
\(\hsame\)-matching unary histories to their denominators preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
Unpack the classifier witness into the two endpoint carriers and the sign,
numerator, and denominator sameness fields. Close both endpoint denominator
carriers under unary prepend, transporting unary membership of the first prefix
across prefix sameness for the second endpoint. The resulting denominator
sameness follows by eliminating the original denominator and prefix sameness
witnesses and applying reflexivity to the resulting append history.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_prepend\_unary\_denominators\_closed}

\begin{theorem}[Rat classifier unary denominator context closure]
\label{thm:rat-classifier-append-unary-denominator-context-closed}
If two rational representatives are classified the same, then surrounding their
denominators by $\hsame$-matching unary prefixes and unary tails preserves the
rational classifier relation.
\end{theorem}
\begin{proof}
First apply denominator append closure to the classified representatives and
the matching unary tails. Then apply denominator prepend closure to the
resulting classified representatives and the matching unary prefixes. The sign
and numerator witnesses are unchanged, while the denominator endpoint relation
is obtained by the two concrete unary-context closure steps.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_append\_unary\_denominator\_context\_closed}

\begin{theorem}[Rat classifier transitivity]
\label{thm:rat-classifier-transitivity}
If one rational representative is classified the same as a second representative, and the second representative is classified the same as a third representative, then the first and third representatives are classified the same.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_trans}
\begin{proof}
Unpack both classifier witnesses. The endpoint carriers are preserved, while sign sameness and the two history-sameness components compose by the finite-kernel transitivity theorems for \(\msame\) and \(\hsame\).
\end{proof}

\begin{theorem}[Rat classifier symmetry]
\label{thm:rat-classifier-symmetry}
If one rational representative is classified the same as a second representative,
then the second representative is classified the same as the first.
\end{theorem}
\begin{proof}
Unpack the endpoint carriers and the sign, numerator, and denominator sameness
fields. Rebuild the classifier in the reverse direction using symmetry of
\(\msame\) for signs and symmetry of \(\hsame\) for both history components.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_symm}

\begin{theorem}[Rat classifier component transport]
\label{thm:rat-classifier-component-transport}
If both rational classifier endpoints are transported componentwise by
\(\msame\) on signs and \(\hsame\) on numerator and denominator histories,
then the rational classifier transports to the componentwise transported
representatives.
\end{theorem}
\begin{proof}
Unpack the rational classifier witness. Transport each endpoint rational
carrier by the component transport theorem, then compose the old sign,
numerator, and denominator sameness links with the reversed source endpoint
transports and the target endpoint transports.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatClassifierSpec\_component\_transport}

\begin{theorem}[Rat history classifier one-tail exactness]
\label{thm:rat-history-classifier-e1-tail-unary-iff}
For denominator tails \(d,e:\mathsf{BHist}\), the rational history classifier
relates the one-extension denominators exactly when both tails are unary and
internally the same:
$$
\mathsf{RatHistoryClassifier}(\Eone(d),\Eone(e))
\Longleftrightarrow
\mathsf{Unary}(d)\land \mathsf{Unary}(e)\land \hsame(d,e).
$$
\end{theorem}
\begin{proof}
For the forward direction, unpack the classifier into two rational history
carrier witnesses and the endpoint \(\hsame\) link. The one-tail carrier
equivalence extracts unary membership of both tails, and \(\Eone\)-constructor
inversion gives \(\hsame(d,e)\). For the reverse direction, rebuild both
rational history carriers from the unary tails and lift \(\hsame(d,e)\) by
\(\Eone\)-congruence.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_e1\_tail\_unary\_iff}

\begin{theorem}[Rat history classifier exposes positive denominators]
\label{thm:rat-history-classifier-positive-denominators}
If denominator histories $d$ and $e$ are related by the rational history
classifier, then both $d$ and $e$ carry positive unary denominator witnesses.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into its two endpoint rational-history
carrier witnesses and the stored denominator $\hsame$ link. Convert each
endpoint carrier to a positive unary denominator witness by the rational history
carrier positive-denominator equivalence.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_positive\_denominators}

\begin{theorem}[Rat history classifier endpoints are nonempty]
\label{thm:rat-history-classifier-endpoints-not-empty}
If denominator histories $d$ and $e$ are related by the rational history
classifier, then neither endpoint is internally the same as the empty history:
$$
(\hsame(d,\emp)\to\mathsf{False})\land
(\hsame(e,\emp)\to\mathsf{False}).
$$
\end{theorem}
\begin{proof}
Unpack the rational history classifier into its two endpoint rational-history
carrier witnesses. Apply rational-history carrier nonemptiness to each endpoint
carrier.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_endpoints\_not\_empty}

\begin{theorem}[Rat history classifier transitivity]
\label{thm:rat-history-classifier-trans}
If denominator histories $d$ and $e$ are related by the rational history
classifier, and $e$ and $f$ are related by the same classifier, then $d$ and
$f$ are related by the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the two rational history classifier witnesses. Keep the left endpoint
carrier from the first witness and the right endpoint carrier from the second
witness, then compose the denominator history sameness proofs by transitivity
of $\hsame$.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_trans}

\begin{theorem}[Rat history classifier endpoint transport]
\label{thm:rat-history-classifier-hsame-transport}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, and \(d\) and \(e\) are respectively internally the same as
\(d'\) and \(e'\), then \(d'\) and \(e'\) are related by the rational history
classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint rational-history carriers
and the stored \(\hsame(d,e)\) link. Transport both endpoint carriers across
the supplied history-sameness witnesses, then compose the reversed
\(\hsame(d,d')\) link, the stored classifier link, and \(\hsame(e,e')\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_hsame\_transport}

\begin{theorem}[Rat history classifier symmetry]
\label{thm:rat-history-classifier-symmetry}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, then \(e\) and \(d\) are related by the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier witness. Swap the two endpoint carrier
witnesses, and reverse the denominator history-sameness proof by symmetry of
\(\hsame\).
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_symm}

\begin{theorem}[Rat history classifier unary denominator append closure]
\label{thm:rat-history-classifier-append-unary-denominator-closed}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, and unary tails \(t_d\) and \(t_e\) satisfy \(\hsame(t_d,t_e)\),
then appending the tails to the corresponding denominator histories preserves
the rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint carriers and denominator
\(\hsame\). Close the left endpoint carrier under unary denominator append.
Transport unary membership from \(t_d\) to \(t_e\), close the right endpoint
carrier under append, and combine the denominator \(\hsame\) with the tail
\(\hsame\) by constructor cases on append.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_append\_unary\_denominator\_closed}

\begin{theorem}[Rat history classifier unary denominator prepend closure]
\label{thm:rat-history-classifier-prepend-unary-denominator-closed}
If denominator histories $d$ and $e$ are related by the rational history
classifier, and unary prefixes $p_d$ and $p_e$ satisfy $\hsame(p_d,p_e)$, then
prepending the prefixes to the corresponding denominator histories preserves the
rational history classifier.
\end{theorem}
\begin{proof}
Unpack the rational history classifier into endpoint carriers and denominator
$\hsame$. Close the left endpoint carrier under unary denominator prepend.
Transport unary membership from $p_d$ to $p_e$, close the right endpoint carrier
under prepend, and combine the denominator and prefix $\hsame$ witnesses by
constructor cases on the continuation append operation.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_prepend\_unary\_denominator\_closed}

\begin{theorem}[Rat history classifier unary denominator context closure]
\label{thm:rat-history-classifier-unary-denominator-context-closed}
If denominator histories \(d\) and \(e\) are related by the rational history
classifier, unary prefixes \(p_d,p_e\) satisfy \(\hsame(p_d,p_e)\), and unary
tails \(t_d,t_e\) satisfy \(\hsame(t_d,t_e)\), then placing the matching prefix
and tail around the corresponding denominators preserves the rational history
classifier.
\end{theorem}
\begin{proof}
First apply unary denominator append closure to the classified denominator
histories and the matching tails. Then apply unary denominator prepend closure
to the resulting classified denominator histories and the matching prefixes.
The endpoint carrier witnesses are closed by the two concrete unary closure
steps, and the denominator relation is the composed \(\hsame\)-respecting
append context.
\end{proof}
\leanchecked{BEDC.Derived.RatUp.RatHistoryClassifier\_unary\_denominator\_context\_closed}

\begin{definition}[Rat stability certificate]
\label{def:rat-stability-certificate}
The stability certificate consists of:
\begin{enumerate}
  \item normalization produces positive denominator
  \item normalization produces coprime pair
  \item normalization is idempotent
  \item structural reflexivity and transitivity
  \item positive denominator closure under unary prefix continuation
  \item closure of rational operations after re-normalization
\end{enumerate}
\end{definition}

\begin{definition}[Rat ledger policy]
\label{def:rat-ledger-policy}
Record the raw rational-history carrier and an $\hsame$ link to the visible denominator history.
\end{definition}
\leandef{BEDC.Derived.RatUp.RatHistoryLedgerPolicy}

\begin{theorem}[Rat ledger visible carrier]
\label{thm:rat-ledger-visible-carrier}
If a raw rational history satisfies the ledger policy for a visible history, then the visible history is itself a rational-history carrier.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_visible\_carrier}
\begin{proof}
Unpack the ledger policy into a raw rational-history carrier and an $\hsame$ link from the raw history to the visible history. Transport the raw carrier across that link.
\end{proof}

\begin{theorem}[Rat ledger visible positive denominator readback]
\label{thm:rat-ledger-visible-positive-denominator-readback}
If $\mathsf{RatHistoryLedgerPolicy}(\rho,v)$ holds and
$\hsame(v,\mathsf{e1}(t))$ holds, then $\mathsf{UnaryHistory}(t)$ holds.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_visible\_positive\_denominator\_readback}
\begin{proof}
The ledger visible-carrier theorem transports the raw rational-history carrier
to $v$. Transport that carrier once more across $\hsame(v,\mathsf{e1}(t))$ and
apply the one-extension rational-history carrier characterization.
\end{proof}

\begin{theorem}[Rat ledger append unary denominator closure]
\label{thm:rat-ledger-append-unary-denominator-closed}
If $\mathsf{RatHistoryLedgerPolicy}(\rho,v)$ holds, $\mathsf{UnaryHistory}(t)$
holds, and $\hsame(t,t')$ holds, then appending those unary denominator tails
preserves the rational ledger:
$$
\mathsf{RatHistoryLedgerPolicy}(\mathsf{append}(\rho,t),\mathsf{append}(v,t')).
$$
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_append\_unary\_denominator\_closed}
\begin{proof}
Unpack the ledger into a raw rational-history carrier and an $\hsame(\rho,v)$
link. The denominator-append carrier theorem closes the raw endpoint under the
unary tail, and the two $\hsame$ links identify the appended raw and visible
histories.
\end{proof}

\begin{theorem}[Rat ledger history-sameness transport]
\label{thm:rat-ledger-hsame-transport}
If a rational ledger relates raw and visible histories, then transporting the
raw endpoint and the visible endpoint along \(\hsame\) yields another rational
ledger relation.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_hsame\_transport}
\begin{proof}
Unpack the ledger into a raw carrier and a raw-visible link. Transport the raw
carrier across the raw-endpoint link, then compose the reversed raw transport
link, the stored ledger link, and the visible-endpoint link.
\end{proof}

\begin{theorem}[Rat ledger raw-visible classifier]
\label{thm:rat-ledger-raw-visible-classifier}
If $\mathsf{RatHistoryLedgerPolicy}(\rho,v)$ holds, then
$\mathsf{RatHistoryClassifier}(\rho,v)$ holds.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_raw\_visible\_classifier}
\begin{proof}
Unpack the ledger into the raw rational-history carrier for $\rho$ and the
stored $\hsame(\rho,v)$ link. The visible-carrier theorem supplies the
rational-history carrier for $v$, and these witnesses form the raw-visible
rational history classifier.
\end{proof}

\begin{theorem}[Rat ledger classifier extension]
\label{thm:rat-ledger-classifier-extension}
If $\mathsf{RatHistoryLedgerPolicy}(\rho,v)$ holds and
$\mathsf{RatHistoryClassifier}(v,t)$ holds, then
$\mathsf{RatHistoryClassifier}(\rho,t)$ holds.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_classifier\_extension}
\begin{proof}
Convert the raw-visible ledger into the raw-visible classifier, then compose it
with the visible-target classifier by transitivity.
\end{proof}

\begin{theorem}[Rat history ledger classifier endpoint equivalence]
\label{thm:rat-history-ledger-classifier-endpoint-equivalence}
If $\mathsf{RatHistoryLedgerPolicy}(\rho,v)$ holds, then every target history
$w$ is classified from $\rho$ exactly when it is classified from $v$:
$$
\mathsf{RatHistoryClassifier}(\rho,w)\leftrightarrow
\mathsf{RatHistoryClassifier}(v,w).
$$
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.RatHistoryLedgerPolicy\_classifier\_endpoint\_equivalence}
\begin{proof}
The ledger supplies the raw-visible rational classifier. For the raw-to-visible
direction, reverse that classifier by symmetry and compose it with the
raw-target classifier by transitivity. The visible-to-raw direction is the
ledger classifier extension theorem.
\end{proof}

\begin{definition}[\(\RatUp\) certificate obligations]
\label{def:rat-certificate-obligations}
The carrier, source, pattern, classifier, stability, and ledger data listed above are the obligations required for the interface name \(\RatUp\).
\end{definition}

\begin{theorem}[Concrete \(\RatUp\) naming certificate]
\label{thm:concrete-rat-namecert}
The rational-history carrier/classifier tuple forms a valid semantic naming certificate for $\RatUp$ at the history level.
\end{theorem}
\leanchecked{BEDC.Derived.RatUp.rat\_history\_semantic\_name\_certificate}

\begin{corollary}[\(\RatUp\) is licensed, not primitive]
\label{cor:rat-licensed-not-primitive}
\(\RatUp\) is licensed by normalized representatives, not by a quotient of pairs.
\end{corollary}

\paragraph{Primitive boundary.}
\(\RatUp\) is not a BEDC primitive. It is admitted only when those obligations are supplied.

\begin{remark}[Zero-axiom encoding note]
\label{rem:rat-zero-axiom-note}
Replaces quotient equivalence and \(\mathsf{Quot.sound}\) with canonical normalization.
\end{remark}
