\chapter{A Concrete Naming Certificate for $\FormalConstantEmpiricalValueBoundaryUp$}
\label{ch:concrete-instances-formalconstantempiricalvalueboundary-namecert}
\origin{ai-composite}

The $\FormalConstantEmpiricalValueBoundaryUp$ packet realizes the boundary in \autoref{subsec:philosophy-formal-constants-empirical-values} as a finite NameCert surface. It sits after the cross-history causal-rate carrier of \autoref{ch:concrete-instances-crosshistcausalrate-namecert}, the maximum-rate bound carrier of \autoref{ch:concrete-instances-maxcausalrate-namecert}, the unit-calibration ledger of \autoref{ch:concrete-instances-unit-calibration-ledger-namecert}, and the empirical-regularity persistence carrier of \autoref{ch:concrete-instances-empirical-regularity-persistence-namecert}. Those siblings expose invariant rate form, unary maximum-bound rows, unit and calibration records, and empirical persistence records; this packet binds them without collapsing formal invariant form into measured numerical value.

\begin{definition}[Formal-constant empirical-value boundary carrier]
\label{def:formal-constant-empirical-value-boundary-carrier}
A $\FormalConstantEmpiricalValueBoundaryUp$ carrier is a finite $\BHist$ packet
$$
K=(F,E,U,I,R,G,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $F$ is the formal invariant-form row, read through $\CrossHistCausalRateUp$ and $\MaxCausalRateUp$, exposing only observer-symmetric bound form, unary comparison, no-global-frame discipline, and structural transport.
\item $E$ is the empirical measurement ledger row, read through $\EmpiricalRegularityPersistenceUp$, exposing observed records, measurement protocol, classifier, error ledger, and persistence-facing failure branch.
\item $U$ is the unit-calibration row, read through $\UnitCalibrationLedgerUp$, exposing unit convention, calibration standard, conversion route, uncertainty budget, and instrument ledger.
\item $I$ is the uncertainty and instrument row binding error bars, instrument identity, resolution limits, and finite replay of the measurement route.
\item $R$ is the reproducibility row recording repeated finite observation packets, accepted classifier agreement, rejected runs, and displayed continuation routes for remeasurement.
\item $G$ is the failure row recording missing calibration, incompatible units, instrument defeat, reproducibility failure, detached invariant form, and detached empirical value.
\item $H$ records componentwise $\hsame$ transport for $F,E,U,I,R,G,C,P,N$.
\item $C$ records displayed $\Cont$ routes for invariant-form readback, measurement replay, calibration replay, uncertainty reading, reproducibility replay, and failure consumption.
\item $P$ is the $\Pkg$ provenance over $\FormalConstantEmpiricalValueBoundaryUp$, $\CrossHistCausalRateUp$, $\MaxCausalRateUp$, $\UnitCalibrationLedgerUp$, $\EmpiricalRegularityPersistenceUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\FormalConstantEmpiricalValueBoundaryUp}$ row.
\end{enumerate}
The carrier has no coordinate for extracting a numerical empirical value from $F$ alone, for promoting $E,U,I,R$ to a structural invariant without $F$, or for reading a physical constant without the failure row $G$.
\end{definition}

\begin{theorem}[Formal-constant empirical-value boundary NameCert obligations]
\label{thm:formal-constant-empirical-value-boundary-namecert-obligations}
For the carrier of \autoref{def:formal-constant-empirical-value-boundary-carrier}, the local $\NameCert_{\FormalConstantEmpiricalValueBoundaryUp}$ surface consists exactly of formal invariant-form exposure through $F$, empirical measurement exposure through $E$, unit-calibration exposure through $U$, uncertainty and instrument exposure through $I$, reproducibility exposure through $R$, failure exposure through $G$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.FormalConstantEmpiricalValueBoundaryUp.FormalConstantEmpiricalValueBoundaryTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier $K=(F,E,U,I,R,G,H,C,P,N)$. The first row exposes the structural side of the boundary: observer-symmetric invariant form, maximum-rate bound form, unary comparison, and no-global-frame discipline.

Read the empirical side through $E,U,I,R$. These rows display measurement records, unit convention, calibration, instrument and uncertainty data, and reproducibility evidence as finite ledger coordinates rather than as consequences of the invariant-form row.

The failure row $G$ records every way the two sides can be detached. Missing unit calibration, incompatible units, instrument defeat, reproducibility failure, a bare invariant form, and a bare empirical value are all visible refusal branches.

The structural rows $H,C,P,N$ preserve and replay only the displayed packet. Since no further coordinate is present, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Formal-constant empirical-value noncollapse]
\label{thm:formal-constant-empirical-value-boundary-noncollapse}
An accepted $\FormalConstantEmpiricalValueBoundaryUp$ carrier permits a consumer to compare a formal constant with an empirical value only through the full packet
$$
F,E,U,I,R,G,H,C,P,N .
$$
The formal invariant-form row $F$ cannot supply the empirical numerical value, and the empirical rows $E,U,I,R$ cannot supply the structural invariant form. A physical-law or rate-facing consumer must preserve the boundary row $G$ and the local $\NameCert$ row $N$ before citing the packet.
\end{theorem}
\begin{proof}
Use \autoref{thm:formal-constant-empirical-value-boundary-namecert-obligations}. It separates invariant-form exposure from measurement, calibration, instrument, and reproducibility exposure.

The row $F$ is inherited from the cross-history causal-rate and maximum-rate surfaces. Those packets expose structural bound form and no-global-frame discipline, but they carry no unit convention, instrument ledger, uncertainty budget, or reproducibility ledger.

The rows $E,U,I,R$ are empirical rows. They provide measured records, unit calibration, uncertainty, and reproducibility, but they do not create the observer-symmetric invariant-form row supplied by $F$.

Finally read $G,H,C,P,N$. The failure row records every attempted collapse as a visible boundary case, while transport, continuation, provenance, and local naming preserve the same finite packet. Thus comparison is available only as a noncollapse boundary, not as an identification of formal constants with empirical values.
\end{proof}

\falsifiablePrediction{A physical-law consumer that reads a numerical empirical value from invariant form alone refutes the $\FormalConstantEmpiricalValueBoundaryUp$ packet.}

\independenceWitness{crosshistcausalrate, maxcausalrate, unitcalibrationledger, empiricalregularitypersistence: $\FormalConstantEmpiricalValueBoundaryUp$ is not bijective to any listed sibling because it carries formal invariant form, measurement ledger, unit calibration, uncertainty, instrument, reproducibility, failure, transport, continuation, provenance, and local naming rows in one finite boundary packet.}

\begin{closurestatus}{\FormalConstantEmpiricalValueBoundaryUp}
  \constructivestory{A $\FormalConstantEmpiricalValueBoundaryUp$ packet is generated by first displaying the formal invariant-rate rows and then attaching empirical measurement, unit-calibration, uncertainty, instrument, reproducibility, failure, transport, continuation, package, and local naming rows in one finite $\BHist$ carrier. The classifier is not allowed to identify the formal row with the measured rows; it reads each coordinate through componentwise $\hsame$ and the visible $\Cont$ replay routes. The ledger story is therefore a boundary story: empirical values may be compared to invariant form only through the recorded calibration and reproducibility rows, while failed attempts to collapse the two sides remain visible as the failure coordinate.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the carrier definition, NameCert-obligation theorem, noncollapse theorem, falsifiable prediction, and independence witness for $\FormalConstantEmpiricalValueBoundaryUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{It does not claim host physical equality, extraction of a numerical value from invariant form alone, or promotion of empirical ledgers into structural constants.}
  \upgradepath{To reach obligationClosure, the finite boundary carrier and noncollapse obligations must be mirrored by Lean definitions and checked transport theorems.}
\end{closurestatus}
