\chapter{A Concrete Naming Certificate for $\UseRuleLedgerUp$}
\label{ch:concrete-instances-use-rule-ledger-namecert}
\origin{ai}

The $\UseRuleLedgerUp$ packet realizes the certified-use reading of \autoref{subsec:philosophy-wittgenstein-use} as a finite NameCert carrier. It sits beside the machine-facing boundary of \autoref{ch:concrete-instances-machine-interface-boundary-namecert}, the registry export surface of \autoref{ch:concrete-instances-registry-export-surface-namecert}, the apophatic naming boundary of \autoref{ch:concrete-instances-apophaticname-namecert}, and the kernel audit witness of \autoref{ch:concrete-instances-kernelauditwitness-namecert}. Those siblings expose machine routing, export control, refused supply, and accepted audit evidence; this packet binds use, rule-following, source/classifier rows, stability, ledger policy, public audit, transport, continuation, provenance, and local naming before a name-use is licensed.

\begin{definition}[Use-rule ledger carrier]
\label{def:use-rule-ledger-carrier}
A $\UseRuleLedgerUp$ carrier is a finite $\BHist$ packet
$$
G=(U,R,S,C,L,A,H,Q,P,N)
$$
whose displayed rows have the following roles:
\begin{enumerate}
\item $U$ is the use-event row, recording the name, item used, local history, and requested public reading.
\item $R$ is the rule row, recording the use rule by which the name may be applied to the item.
\item $S$ is the source/classifier row, recording the displayed source field and classifier that check the item against the licensed name.
\item $C$ is the stability row, recording the finite stability evidence under which the same use may be replayed.
\item $L$ is the ledger row, recording the hidden-material policy, refused supply, and visible rule-following trace associated with the use.
\item $A$ is the public audit row, recording the machine-interface boundary, registry-export surface, apophatic naming boundary, and kernel audit witness consulted by the use.
\item $H$ records componentwise $\hsame$ transport for the use event, rule, source/classifier, stability, ledger, audit, continuation, provenance, and local naming rows.
\item $Q$ records displayed $\Cont$ replay for the certified-use route.
\item $P$ is the $\Pkg$ provenance over $\UseRuleLedgerUp$, $\MachineInterfaceBoundaryUp$, $\RegistryExportSurfaceUp$, $\ApophaticNameUp$, $\KernelAuditWitnessUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\UseRuleLedgerUp}$ row.
\end{enumerate}
The carrier has no coordinate for private meaning, bare reference, unclassified social habit, unledgered rule-following, hidden source supply, or a name-use licensed only by prose adjacency.
\end{definition}

\begin{theorem}[Use-rule ledger NameCert obligations]
\label{thm:use-rule-ledger-namecert-obligations}
For the carrier of \autoref{def:use-rule-ledger-carrier}, the local $\NameCert_{\UseRuleLedgerUp}$ obligation surface consists exactly of carrier admission for $G=(U,R,S,C,L,A,H,Q,P,N)$, use-event exposure through $U$, rule exposure through $R$, source/classifier exposure through $S$, stability exposure through $C$, ledger exposure through $L$, public audit exposure through $A$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $Q$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier into its ten displayed rows. The use event, rule, source/classifier, stability, and ledger rows are read before the public audit route is consumed, so a licensed use cannot be recovered from an audit citation alone.

The audit row records the machine-interface boundary, registry-export surface, apophatic naming boundary, and kernel audit witness. These siblings explain where the use is checked, exported, refused, or read back, but they do not replace the displayed use, rule, source/classifier, stability, and ledger rows.

Finally $H,Q,P,N$ transport, replay, source, and name the same finite packet. Since the carrier contains no hidden source coordinate and no prose-only licensing coordinate, the listed rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Certified-use route]
\label{thm:use-rule-ledger-certified-use-route}
Every accepted $\UseRuleLedgerUp$ route that licenses a public name-use must expose the use-event row $U$, rule row $R$, source/classifier row $S$, stability row $C$, ledger row $L$, public audit row $A$, transport row $H$, continuation row $Q$, provenance row $P$, and local naming row $N$. A route that omits any one of these rows is at most a projection of the use-rule ledger, not the accepted carrier of \autoref{def:use-rule-ledger-carrier}.
\end{theorem}
\begin{proof}
Begin with the displayed packet $G=(U,R,S,C,L,A,H,Q,P,N)$. The name-use is located by $U$, governed by $R$, constrained by $S$, stabilized by $C$, and ledgered by $L$ before any consumer can read it as public.

The public audit row $A$ then records the sibling boundary surfaces. It can route the packet to machine-facing, registry-facing, apophatic, and kernel-audit consumers, but those consumers only see the use after the preceding rows have already licensed it.

The structural rows $H,Q,P,N$ preserve the same packet under transport, continuation replay, provenance, and naming. Omitting one of the displayed rows therefore changes the carrier into a projection rather than an accepted certified-use route.
\end{proof}

\begin{theorem}[Use-rule ledger nonescape boundary]
\label{thm:use-rule-ledger-nonescape-boundary}
No accepted $\UseRuleLedgerUp$ packet may turn a missing source/classifier row, missing stability row, or missing ledger/audit row into licensed use by appealing to private meaning, social repetition, machine export, registry presence, apophatic refusal, or kernel readback alone.
\end{theorem}
\begin{proof}
Inspect the licensing rows $S,C,L,A$. The source/classifier row states what item is being used under what name; the stability row states when the same use is replayable; the ledger row records hidden-material and rule-following policy; and the audit row states how the public route is checked.

Private meaning and social repetition are not coordinates of the carrier. Machine export, registry presence, apophatic refusal, and kernel readback appear only through $A$ and $P$, where they are dependencies of the displayed packet rather than substitutes for the licensing rows.

Thus a missing source/classifier, stability, ledger, or audit row cannot be supplied by another route. The nonescape boundary is the requirement that certified use remains attached to the finite rows that license it.
\end{proof}

\begin{theorem}[Use-rule ledger TasteGate obligation]
\label{thm:use-rule-ledger-tastegate-obligation}
Any TasteGate admission for $\UseRuleLedgerUp$ must preserve nontriviality and field faithfulness for the displayed rows $U,R,S,C,L,A,H,Q,P,N$. In particular, admission must distinguish use event, rule, source/classifier, stability, ledger, public audit, transport, continuation, provenance, and local naming rather than collapsing certified use into a single registry or machine-interface row.
\end{theorem}
\leanchecked{BEDC.Derived.UseRuleLedgerUp.UseRuleLedgerTasteGate\_single\_carrier\_alignment}

\begin{proof}
A TasteGate admission reads the carrier as a candidate public object. Nontriviality requires the carrier to exhibit a real row packet, while field faithfulness requires the named fields to remain separately readable by downstream consumers.

Apply this to $G=(U,R,S,C,L,A,H,Q,P,N)$. Collapsing the use event into the rule, the source/classifier into the stability row, or the audit route into machine or registry export would erase a displayed coordinate of certified use.

Therefore the TasteGate obligation is to keep the ten rows distinct while allowing their joint package to be named. The Lean side must provide $\Nontrivial\ \UseRuleLedgerUp$ and $\FieldFaithful\ \UseRuleLedgerUp$ instances in \texttt{lean4/BEDC/Derived/UseRuleLedgerUp/TasteGate.lean} before any checked marker for this carrier can be cited.
\end{proof}

\falsifiablePrediction{Any accepted $\UseRuleLedgerUp$ route that licenses a name-use without the displayed source/classifier, stability, and ledger rows refutes the carrier.}

\independenceWitness{machineinterfaceboundary, registryexportsurface, apophaticname, kernelauditwitness: none is bijective because $\UseRuleLedgerUp$ binds certified use, rule-following, source/classifier, stability, and ledger rows as one name-use packet rather than only routing exports, refusing supply, or reading audit evidence.}

\closureat{UseRuleLedgerUp}{seedStr}
\closureat{UseRuleLedgerUp}{obligationStr}

\begin{closurestatus}{\UseRuleLedgerUp}
  \constructivestory{A $\UseRuleLedgerUp$ packet is generated from displayed use rows, rule rows, witness rows, audit rows, componentwise $\hsame$ transport, displayed $\Cont$ replay, package provenance, and local naming in one finite $\BHist$ carrier. The classifier licenses rule-following only when the use, rule, witness, and audit coordinates are present together; social repetition and prose adjacency are not enough. The ledger story is a public rule route: a certified-use consumer reads the same finite packet through transport and continuation rows, while hidden source supply, private meaning, and unledgered rule-following remain outside the carrier inventory.}
  \theoryclosure{\seedClosure}
  \scopeclosed{This chapter binds the carrier definition, NameCert-obligation, certified-use-route, nonescape-boundary, TasteGate-obligation, independence witness, and existing closure annotations for $\UseRuleLedgerUp$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{It does not claim private meaning, bare reference, unclassified social habit, unledgered rule-following, hidden source supply, or prose-only name-use licensing.}
  \upgradepath{To reach obligationClosure, the use-rule carrier, route theorem, and nonescape boundary must be encoded as checked finite-row obligations.}
\end{closurestatus}
