\chapter{A Concrete Naming Certificate for $\UseProcessLimitLedgerUp$}
\label{ch:concrete-instances-use-process-limit-ledger-namecert}
\origin{ai}

The $\UseProcessLimitLedgerUp$ packet realizes the use, continuation-process, and formal-limit boundary of \autoref{subsec:philosophy-wittgenstein-use}, \autoref{subsec:philosophy-whitehead-process}, and \autoref{cor:philosophy-formal-limit-ground-payment} as one finite export-boundary carrier. It sits beside the registry export surface of \autoref{ch:concrete-instances-registry-export-surface-namecert}, the claim registry layer of \autoref{ch:concrete-instances-claimregistrylayer-namecert}, the kernel acceptance witness of \autoref{ch:concrete-instances-kernelacceptancewitness-namecert}, and the continuation countermodel of \autoref{ch:concrete-instances-continuationcountermodel-namecert}. Those siblings expose export control, claim admission, accepted-declaration evidence, and failed continuation matching; this packet binds certified use, continuation route, formal-limit refusal, transport, replay, provenance, and local naming before any philosophy-facing consumer may read use as exported BEDC content.

\begin{definition}[Use-process-limit ledger carrier]
\label{def:use-process-limit-ledger-carrier}
A $\UseProcessLimitLedgerUp$ carrier is a finite $\BHist$ packet
$$
L=(U,C,L_f,H,R,P,N)
$$
with seven displayed rows:
\begin{enumerate}
\item $U$ is the certified-use row, recording the public use of the named item together with the $\NameCert$ legitimacy data that separates licensed use from private image, bare reference, or unregistered habit;
\item $C$ is the continuation-process row, recording the displayed $\Cont$ route through which the certified use is replayed as a process before any export is accepted;
\item $L_f$ is the formal-limit row, recording refusal to internalize total truth, host equality, halting decision, or a closed open-meta-loop witness;
\item $H$ is the componentwise $\hsame$ transport row for certified use, continuation process, formal-limit refusal, replay, provenance, and local naming;
\item $R$ is the displayed $\Cont$ replay row that shows downstream consumers the same use/process/refusal route rather than a detached use token;
\item $P$ is the $\Pkg$ provenance row over $\NameCert$, $\Cont$, $\RegistryExportSurfaceUp$, $\ClaimRegistryLayerUp$, $\KernelAcceptanceWitnessUp$, and the source vision of \autoref{ch:visions-philosophy-traditions};
\item $N$ is the local $\NameCert_{\UseProcessLimitLedgerUp}$ row.
\end{enumerate}
The carrier has no coordinate for an unlicensed use oracle, process-free export, total truth predicate, host equality, closed meta loop, or tradition identity collapse.
\end{definition}

\begin{theorem}[Use-process-limit ledger NameCert obligations]
\label{thm:use-process-limit-ledger-namecert-obligations}
For the carrier of \autoref{def:use-process-limit-ledger-carrier}, the local $\NameCert_{\UseProcessLimitLedgerUp}$ surface has exactly three primary obligation rows before transport, replay, and provenance are consumed: certified use through $U$, continuation process through $C$, and formal-limit refusal through $L_f$. The rows $H,R,P,N$ transport, replay, source, and locally name that three-row surface without adding a fourth philosophy-side authority.
\end{theorem}
\begin{proof}
Project the finite packet $L=(U,C,L_f,H,R,P,N)$. The first three rows display the certified-use, continuation-process, and formal-limit-refusal obligations that a NameCert consumer is allowed to inspect.

The transport row $H$ and replay row $R$ preserve those same displayed rows. They do not add a private meaning row, a process-free route, or a host-side completion coordinate.

Finally $P$ records the registry, claim, kernel-acceptance, and source-vision provenance, while $N$ gives the local NameCert row. Since both rows cite the same three primary obligations, the listed surface exhausts the local NameCert obligations.
\end{proof}

\begin{theorem}[Use-process-limit ledger export boundary]
\label{thm:use-process-limit-ledger-export-boundary}
Every accepted $\UseProcessLimitLedgerUp$ export presents certified use, continuation process, and formal-limit refusal as one finite packet. An export that presents $U$, $C$, and $L_f$ as three detachable exports is rejected by the carrier, even if each detached row is individually named.
\end{theorem}
\begin{proof}
Read the export through the carrier, not through isolated row names. The rows $U,C,L_f$ are fields of the same finite packet, and the downstream route reads them only through the shared transport, replay, provenance, and local naming rows $H,R,P,N$.

If a proposed export detaches certified use from process, it deletes the route that makes use replayable. If it detaches use and process from formal-limit refusal, it allows the consumer to read licensed use as total truth, host equality, halting decision, or closed meta-loop completion.

Thus an accepted export must preserve the packet boundary. Three separately named exports can cite parts of the vocabulary, but they are not an export of \autoref{def:use-process-limit-ledger-carrier}.
\end{proof}

\begin{theorem}[Use-process-limit ledger sibling independence]
\label{thm:use-process-limit-ledger-sibling-independence}
The $\UseProcessLimitLedgerUp$ carrier is not bijective, under NameCert-row preservation, to $\RegistryExportSurfaceUp$, $\ClaimRegistryLayerUp$, $\KernelAcceptanceWitnessUp$, reflective-stability packets, or $\ContinuationCountermodelUp$. Each sibling omits at least one of certified use, continuation-process route, formal-limit refusal, componentwise transport, displayed replay, provenance, and local naming as one carrier.
\end{theorem}
\begin{proof}
Compare displayed rows. $\RegistryExportSurfaceUp$ controls registry export, $\ClaimRegistryLayerUp$ admits or refuses package claims, $\KernelAcceptanceWitnessUp$ records accepted kernel declarations, reflective-stability packets track stability of reflection routes, and $\ContinuationCountermodelUp$ records a continuation mismatch.

None of those siblings simultaneously carries $U,C,L_f,H,R,P,N$. In particular, an export surface can omit certified use, a claim layer can omit the continuation route, a kernel witness can omit the philosophy-side formal-limit refusal, a stability packet can omit the local use ledger, and a countermodel can omit accepted export provenance.

Therefore no sibling is bijective to $\UseProcessLimitLedgerUp$ while preserving local NameCert rows. A bijection would have to recover every displayed coordinate of the packet from a sibling that lacks at least one such coordinate.
\end{proof}

\falsifiablePrediction{Any accepted use-process-limit export that treats certified use, continuation-process, and formal-limit refusal as three detachable exports refutes the packet.}

\independenceWitness{registryexportsurface, claimregistrylayer, kernelauditwitness, reflectivestability, continuationcountermodel: none is bijective because each omits at least one of certified-use, process-route, formal-limit refusal, transport, replay, provenance, and local naming as one carrier.}

The Lean follow-up must provide $\Nontrivial\ \UseProcessLimitLedgerUp$ and $\FieldFaithful\ \UseProcessLimitLedgerUp$ in \texttt{lean4/BEDC/Derived/UseProcessLimitLedgerUp/TasteGate.lean}. Those instances must preserve $U,C,L_f,H,R,P,N$ as distinct displayed fields before any checked marker can cite \texttt{BEDC.Derived.UseProcessLimitLedgerUp.taste\_gate}.

\closureat{UseProcessLimitLedgerUp}{seedStr}

\begin{closurestatus}{\UseProcessLimitLedgerUp}
  \constructivestory{A $\UseProcessLimitLedgerUp$ packet is generated from certified-use and NameCert-legitimacy data, a continuation-process route, a formal-limit refusal row, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:use-process-limit-ledger-carrier}, \autoref{thm:use-process-limit-ledger-namecert-obligations}, \autoref{thm:use-process-limit-ledger-export-boundary}, and \autoref{thm:use-process-limit-ledger-sibling-independence} bind the finite use-process-limit ledger carrier, obligation surface, export boundary, and sibling independence claim.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close whole-philosophy formal package checking, total truth, host equality, closed meta-loop completion, or collapsed tradition identity.}
  \upgradepath{Obligation closure requires checked carrier admission, field faithfulness, nontriviality, NameCert obligation coverage, export-boundary preservation, and sibling-independence coverage for $U,C,L_f,H,R,P,N$.}
\end{closurestatus}
