\chapter{A Concrete Naming Certificate for $\UseProcessLimitUp$}
\label{ch:concrete-instances-useprocesslimit-namecert}
\origin{ai}

The $\UseProcessLimitUp$ packet realizes the use, process, and limit-facing philosophy surface of \autoref{subsec:philosophy-wittgenstein-use}, \autoref{subsec:philosophy-whitehead-process}, and \autoref{def:philosophy-bedc-process} as one finite NameCert carrier. It sits beside the socket-use ledger of \autoref{ch:concrete-instances-socketuseledger-namecert}, the inward eligibility proof of \autoref{ch:concrete-instances-nameeligibilityproof-namecert}, the machine-facing boundary of \autoref{ch:concrete-instances-machine-interface-boundary-namecert}, and the apophatic naming boundary of \autoref{ch:concrete-instances-apophaticname-namecert}. Those siblings expose visible use, name eligibility, machine export control, and refusal-bearing naming; this packet binds certified use, rule audit, continuation process, and formal-limit refusal before any philosophy-facing export can read meaning as licensed use.

\begin{definition}[Use-process-limit carrier]
\label{def:use-process-limit-carrier}
A $\UseProcessLimitUp$ carrier is a finite $\BHist$ packet
$$
U=(N,U_c,R,P_c,L,H,C,K,N_c)
$$
with the following displayed rows:
\begin{enumerate}
\item $N$ is the name row, recording the public name whose meaning is read only through a certificate-governed use surface;
\item $U_c$ is the certified-use row, recording the licensed use of $N$ together with the source and classifier fields that make the use auditable;
\item $R$ is the rule-checking row, recording the finite audit route that separates certificate-governed use from private image, bare reference, or ordinary social habit;
\item $P_c$ is the process-continuation row, recording the displayed $\Cont$ process through which the use is replayed before object-facing export;
\item $L$ is the formal-limit refusal row, recording that the packet does not internalize total truth, host equality, halting decision, or meta-loop closure;
\item $H$ records componentwise $\hsame$ transport for the name, certified-use, rule-checking, process-continuation, formal-limit refusal, replay, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ replay of the same certified-use and process rows for downstream consumers;
\item $K$ is the $\Pkg$ provenance over $\SocketUseLedgerUp$, $\NameEligibilityProofUp$, $\MachineInterfaceBoundaryUp$, $\ApophaticNameUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N_c$ is the local $\NameCert_{\UseProcessLimitUp}$ row.
\end{enumerate}
The carrier has no coordinate for a private-meaning witness, social-habit oracle, host equality, total truth predicate, halting decision, or closed meta loop.
\end{definition}

\begin{definition}[Use-process-limit classifier]
\label{def:use-process-limit-classifier}
A $\UseProcessLimitUp$ classifier from
$$
U=(N,U_c,R,P_c,L,H,C,K,N_c)
$$
to
$$
U'=(N',U'_c,R',P'_c,L',H',C',K',N'_c)
$$
is a componentwise preservation map that carries the name row to the name row, certified use to certified use, rule audit to rule audit, continuation process to continuation process, formal-limit refusal to formal-limit refusal, $\hsame$ transport to $\hsame$ transport, $\Cont$ replay to $\Cont$ replay, $\Pkg$ provenance to $\Pkg$ provenance, and local NameCert naming to local NameCert naming. A map that preserves the use row while deleting either the rule-checking row or the formal-limit refusal row is not a $\UseProcessLimitUp$ classifier.
\end{definition}

\begin{theorem}[Use-process-limit NameCert obligations]
\label{thm:use-process-limit-namecert-obligations}
For the carrier of \autoref{def:use-process-limit-carrier}, the local $\NameCert_{\UseProcessLimitUp}$ surface has five displayed obligation rows before transport and provenance are consumed: name exposure through $N$, certified-use exposure through $U_c$, rule-checking exposure through $R$, process-continuation exposure through $P_c$, and formal-limit refusal exposure through $L$. The remaining rows $H,C,K,N_c$ transport, replay, source, and locally name exactly that five-row surface.
\end{theorem}
\begin{proof}
Project the finite packet $U=(N,U_c,R,P_c,L,H,C,K,N_c)$. The first five rows display the naming, use, rule audit, process, and refusal obligations before any downstream consumer can read the packet.

The transport row $H$ and replay row $C$ preserve those same displayed rows. They do not add a private meaning coordinate or a host-side completion coordinate.

Finally $K$ records the sibling provenance, and $N_c$ gives the local NameCert row. Since both rows cite the same five displayed obligations, the listed surface exhausts the local NameCert obligations.
\end{proof}

\begin{theorem}[Use-process-limit ledger nonescape]
\label{thm:use-process-limit-ledger-nonescape}
Every accepted $\UseProcessLimitUp$ consumer receives certified use, rule audit, process continuation, formal-limit refusal, transport, replay, provenance, and local naming through the finite rows $U_c,R,P_c,L,H,C,K,N_c$. The same consumer receives no private-meaning witness, social-habit oracle, host equality, total truth predicate, halting decision, or meta-loop closure.
\end{theorem}
\begin{proof}
Read the consumer surface through the carrier. The rows $U_c,R,P_c,L$ display the certified use, audit, continuation, and refusal components, while $H,C,K,N_c$ transport, replay, source, and name them.

The forbidden readings are not fields of the packet. The name row $N$ identifies the public name, but it does not supply a private witness, social oracle, host equality, truth predicate, halting decision, or closed meta loop.

Therefore any accepted consumer can receive only the displayed finite package. A route that claims one of the forbidden readings would require a coordinate absent from \autoref{def:use-process-limit-carrier}.
\end{proof}

\begin{theorem}[Use-process-limit certified-use process interface]
\label{thm:use-process-limit-certified-use-process-interface}
Every accepted $\UseProcessLimitUp$ export factors meaning-as-certified-use through the displayed $\Cont$ process row $P_c$ and replay row $C$ before any export route may cite the local NameCert row $N_c$.
\end{theorem}
\begin{proof}
Start with the certified-use row $U_c$. It licenses the use of $N$, but the carrier places it beside the process-continuation row $P_c$ rather than beside an immediate object-export row.

The replay row $C$ then displays the same continuation route for downstream consumers. This keeps meaning-as-certified-use attached to a visible process before the local naming row is consumed.

The local NameCert row $N_c$ therefore names an already displayed process interface. An export that bypasses $P_c$ or $C$ is not an export of the accepted carrier.
\end{proof}

\falsifiablePrediction{If a UseProcessLimitUp packet exports legitimate use while deleting either the rule-audit row or the formal-limit refusal row, the carrier is refuted.}

\independenceWitness{socketuseledger, nameeligibilityproof, machineinterfaceboundary, apophaticname: none is bijective because UseProcessLimitUp simultaneously binds certified use, rule audit, process continuation, formal-limit refusal, transport, replay, provenance, and local naming.}

The Lean follow-up requires $\Nontrivial\ \UseProcessLimitUp$ and $\FieldFaithful\ \UseProcessLimitUp$ instances in \texttt{lean4/BEDC/Derived/UseProcessLimitUp/TasteGate.lean}. Those instances must preserve $N,U_c,R,P_c,L,H,C,K,N_c$ as distinct displayed fields before any checked marker can cite \texttt{BEDC.Derived.UseProcessLimitUp.TasteGate}.

\closureat{UseProcessLimitUp}{seedStr}
