\chapter{A Concrete Naming Certificate for $\SchemeUp$}
\label{ch:concrete-instances-scheme-namecert}

The scheme interface $\SchemeUp$ packages a locally ringed space that admits an open cover by spectra of commutative rings. It depends on $\NameCert_{\RingedSpaceUp}$ (\autoref{ch:concrete-instances-ringedspace-namecert}) and $\NameCert_{\CommRingUp}$ (\autoref{ch:concrete-instances-commring-namecert}), and is the substrate for affine and projective variety certificates.

\section{Carrier definition}
\label{sec:scheme-carrier}

\begin{theorem}[Scheme carrier obligation]\label{thm:scheme-carrier-obligation}
Every $\NameCert_{\SchemeUp}$ certificate must supply a carrier $C_{\SchemeUp}:\mathsf{BHist}\to\mathsf{Prop}$ whose witnesses consist only of a $\RingedSpaceUp$ source row, certified $\CommRingUp$ affine-chart rows, and the affine-cover ledger. The carrier has no host-level scheme object, host spectrum object, host topological-space primitive, host open-set equality, or external sheafification row.
\end{theorem}
\begin{proof}
Unpack the ten-field $\NameCert$ template. Its source field supplies the locally ringed-space row already named by \autoref{ch:concrete-instances-ringedspace-namecert}, so the base carrier is read as a BEDC history predicate over $\mathsf{BHist}$.

The chapter source sentence names exactly the remaining inputs: certified $\CommRingUp$ affine chart rows and the cover ledger. Each chart is therefore recorded as a certificate row attached to a cover index, not as a host spectrum primitive.

Since the ten-field template has no extra carrier slot after source, classifier, stability, exactness, and ledger are fixed, there is no place for a hidden scheme object. The carrier obligation is precisely the displayed $\mathsf{BHist}$ predicate generated by those source and ledger rows.
\end{proof}
\leanchecked{BEDC.Derived.SchemeUp.SchemeSingletonPackage\_carrier\_source\_obligation}

\begin{theorem}[Scheme classifier obligation]\label{thm:scheme-classifier-obligation}
The $\SchemeUp$ classifier must be a BEDC classifier over $C_{\SchemeUp}$, stable under $\hsame$, and determined by the $\RingedSpaceUp$ classifier together with affine-chart classifier agreement from the certified $\CommRingUp$ chart rows. Two scheme carrier witnesses are identified only when their ringed-space rows match and their affine chart rows agree after the displayed cover-refinement and restriction transports.
\end{theorem}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverLedger\_classifier\_refinement\_transport}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverClassifier\_overlap\_locality}
\leanchecked{BEDC.Derived.SchemeUp.SchemeSingleton\_affine\_cover\_classifier\_locality\_obligation}
\begin{proof}
Use the classifier-choice field of the per-object roadmap template to choose the displayed relation on the carrier from the cited source classifiers. The $\RingedSpaceUp$ row supplies the point, open, section, restriction, and local-ring comparisons visible in the locally-ringed-space source.

For each affine chart, read the endpoint comparison from the $\CommRingUp$ certificate row. On overlaps, transport the two chart rows along the cover-refinement and restriction routes already present in the carrier ledger, then compare the transported chart classifiers.

The stability-obligation field of the same template requires this relation to respect $\hsame$. That stability follows by composing the $\RingedSpaceUp$ transport with the chart-level $\CommRingUp$ transports, so the scheme classifier is determined by those two classifier surfaces and no additional equality.
\end{proof}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineChartLedger\_overlap\_locality\_obligation}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverLedger\_overlap\_classifier\_locality}

\begin{theorem}[Scheme affine-cover obligation]\label{thm:scheme-affine-cover-obligation}
The affine-spectrum cover row of a $\NameCert_{\SchemeUp}$ certificate must provide coverage, restriction compatibility, locality, and gluing data as $\mathsf{Pkg}$ and ledger information. These rows are exactly the cover, exactness, ledger, and consumer-boundary data consumable by $\AffineVarUp$ and $\ProjectiveVarUp$, with no additional host spectrum, quotient-cover, or external variety row.
\end{theorem}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverLedger\_restricted\_global\_soundness}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverLedger\_exactness\_obligation}
\begin{proof}
Read the affine-spectrum cover row already named in the seed scope as a finite $\mathsf{Pkg}$-indexed ledger. Coverage says that every accepted carrier witness is assigned to one of those cover packages together with its $\RingedSpaceUp$ source row and certified $\CommRingUp$ chart row.

Restriction compatibility and locality are the overlap clauses of the same ledger. They record the displayed restriction route, the common overlap witness, and the chart-classifier agreement after transport through the ringed-space and commutative-ring certificate surfaces.

Gluing is then a ledger exactness statement: compatible local chart rows repack into the same $\SchemeUp$ carrier witness, and every consumer readback for $\AffineVarUp$ or $\ProjectiveVarUp$ must pass through those listed packages. Thus the cover, exactness, ledger, and consumer rows named in the chapter are the whole affine-cover obligation surface.
\end{proof}
\leanchecked{BEDC.Derived.SchemeUp.SchemeSingleton\_affine\_cover\_ledger\_exactness}
\leanchecked{BEDC.Derived.SchemeUp.SchemeSingleton\_affine\_cover\_nerve\_empty\_boundary}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverLedger\_restriction\_exactness}

\section{The certificate}
\label{sec:scheme-certificate}

\begin{theorem}[Scheme public NameCert surface]\label{thm:scheme-public-namecert-surface}
The public $\NameCert_{\SchemeUp}$ export is the SemanticNameCert surface whose source is the $\RingedSpaceUp$ row together with certified $\CommRingUp$ affine-chart rows and the affine-cover ledger. Its classifier is the ringed-space classifier together with chart agreement under restriction and refinement. Its exactness and consumer boundary are exactly the carrier, classifier, and affine-cover obligations proved in \autoref{thm:scheme-carrier-obligation}, \autoref{thm:scheme-classifier-obligation}, and \autoref{thm:scheme-affine-cover-obligation}.
\end{theorem}
\leanchecked{BEDC.Derived.SchemeUp.SchemeAffineCoverRow\_semantic\_name\_certificate}

\closureat{SchemeUp}{publicStr}[BEDC.Derived.SchemeUp.SchemeAffineCoverRow\_semantic\_name\_certificate]
\begin{closurestatus}{\SchemeUp}
  \theoryclosure{\publicClosure}
  \scopeclosed{The public surface binds the carrier predicate to $\mathsf{BHist}$, transports it by $\hsame$, records $\mathsf{Cont}$ restriction rows and $\mathsf{Pkg}$ affine-cover ledger rows, and fixes the $\RingedSpaceUp$ source rows, $\CommRingUp$ chart classifier rows, and the $\AffineVarUp$/$\ProjectiveVarUp$ consumer boundary.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.SchemeUp.SchemeAffineCoverRow\_semantic\_name\_certificate}
  \bridgestatus{none}
  \notclaimed{This chapter does not close the standard bridge, full affine or projective variety certificates, or bridgeChecked verification.}
  \upgradepath{The bridgedClosure grade requires an explicit standard bridge for the public $\SchemeUp$ surface.}
\end{closurestatus}
