\chapter{A Concrete Naming Certificate for $\PackageGovernanceExportUp$}
\label{ch:concrete-instances-package-governance-export-namecert}
\origin{ai}

The $\PackageGovernanceExportUp$ packet realizes the philosophy-package cannot-claim, in-place governance, capstone, and export interface of \autoref{subsec:philosophy-package-cannot-claim}, \autoref{subsec:philosophy-package-capstone-policy}, and \autoref{subsec:philosophy-package-export-interface} as one finite NameCert carrier. It sits beside the package carrier of \autoref{ch:concrete-instances-bedc-philosophy-package-namecert}, the claim registry layer of \autoref{ch:concrete-instances-claimregistrylayer-namecert}, the registry export surface of \autoref{ch:concrete-instances-registry-export-surface-namecert}, the audit export firewall of \autoref{ch:concrete-instances-auditexportfirewall-namecert}, and the package map boundary of \autoref{ch:concrete-instances-packagemapboundary-namecert}. Those siblings expose package rows, claim admission, export rows, audit refusal, and map-boundary rows separately; this packet binds them before a philosophy-package governance decision can be read as an exportable NameCert row.

\begin{definition}[Package governance export carrier]
\label{def:package-governance-export-carrier}
A $\PackageGovernanceExportUp$ carrier is a finite $\BHist$ packet
$$
G=(P,R,A,C,E,F,T,M,H,K,Q,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $P$ is the $\BedcPhilosophyPackageUp$ row, recording the package thesis, concept registry, theorem map, gap map, tradition/science map, cannot-claim registry, closure-status row, and audit-policy row consumed by the governance packet.
\item $R$ is the cannot-claim registry row, recording blocked philosophical readings, refusal status, reason, upgrade boundary, and the gate through which $\ClaimRegistryLayerUp$ and $\RegistryExportSurfaceUp$ must read the refusal.
\item $A$ is the in-place governance row, recording the affected registry entry, active label, replacement boundary, status effect, and audit-continuity data for package governance.
\item $C$ is the capstone dependency row, recording the concept, theorem-map, gap-map, tradition/science-map, and closure-status dependencies that license any capstone export.
\item $E$ is the export-grade row, recording reading export, paper synthesis export, component checked export, formal package target, and formal package checked status as displayed grades rather than prose impressions.
\item $F$ is the $\AuditExportFirewallUp$ row, recording the same claim site, positive certificate when present, active failure or refusal when present, consistency gate, and firewall decision.
\item $T$ is the target row, recording the machine-facing route, paper-only route when present, Lean target name when present, and absence of a checked package target when a refusal or missing dependency is active.
\item $M$ is the $\PackageMapBoundaryUp$ row, recording theorem-map, gap-map, tradition-map, scientific-map, and axis-boundary handoff for the same package reading.
\item $H$ records componentwise $\hsame$ transport for package, registry, governance, capstone, export, firewall, target, map-boundary, replay, provenance, and local naming rows.
\item $K$ records displayed $\Cont$ replay for reading $P,R,A,C,E,F,T,M$ without adding a host-side governance override or checked-target shortcut.
\item $Q$ is the $\Pkg$ provenance over $\PackageGovernanceExportUp$, $\BedcPhilosophyPackageUp$, $\ClaimRegistryLayerUp$, $\RegistryExportSurfaceUp$, $\AuditExportFirewallUp$, $\PackageMapBoundaryUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\PackageGovernanceExportUp}$ row.
\end{enumerate}
The carrier has no coordinate for a hidden governance decision, unregistered cannot-claim override, capstone without dependencies, export grade detached from refusal audit, unchecked formal-package target, host equality, quotient import, choice import, or prose-only package promotion.
\end{definition}
\leanchecked{BEDC.Derived.PackageGovernanceExportUp.PackageGovernanceExportTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Package governance export NameCert obligations]
\label{thm:package-governance-export-namecert-obligations}
For the carrier of \autoref{def:package-governance-export-carrier}, the local $\NameCert_{\PackageGovernanceExportUp}$ surface consists exactly of carrier admission for $G=(P,R,A,C,E,F,T,M,H,K,Q,N)$, package exposure through $P$, cannot-claim registry exposure through $R$, in-place governance exposure through $A$, capstone dependency exposure through $C$, export-grade exposure through $E$, firewall readback through $F$, target-route exposure through $T$, package-map boundary exposure through $M$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $K$, package provenance through $Q$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet $G=(P,R,A,C,E,F,T,M,H,K,Q,N)$. The package row $P$ supplies the whole philosophy-package surface, while $R,A,C,E$ display the refusal registry, governance action, capstone dependency set, and export grade before any target route is named.

Next read the sibling audit rows. The firewall row $F$ checks the same claim site against positive and negative certificate data, the target row $T$ records whether a machine-facing or paper-only route is available, and the map-boundary row $M$ keeps theorem, gap, tradition, science, and axis-boundary maps visible.

Finally $H,K,Q,N$ transport, replay, source, and name exactly those displayed rows. Since the carrier contains no hidden governance, export, or target coordinate, the listed rows exhaust the local NameCert obligation surface.
\end{proof}

\begin{theorem}[Package governance export refusal totality]
\label{thm:package-governance-export-refusal-totality}
Every accepted $\PackageGovernanceExportUp$ export decision reads the cannot-claim row $R$ and the audit-firewall row $F$ before projecting the export-grade row $E$, target row $T$, or local naming row $N$. If $R$ contains an active refusal for the package reading, the packet cannot expose that reading as formal package checked or as a checked formal-package target.
\end{theorem}
\begin{proof}
Assume an accepted packet $G=(P,R,A,C,E,F,T,M,H,K,Q,N)$. The refusal row $R$ is displayed before export-grade or target projection, so the reading is first classified as admitted, deferred, partial, or blocked by the cannot-claim registry.

The firewall row $F$ reads the same site against the audit rows. If $R$ carries an active refusal, then $F$ records refusal or certificate conflict for that site rather than an admitted checked-target export.

Rows $E$ and $T$ are therefore downstream of the refusal and firewall reads. They can expose a weaker export grade, a paper-only route, or an absent checked package target, but they have no coordinate that can erase $R$ or $F$. The local naming row $N$ names the factored packet and does not create an independent export path.
\end{proof}

\begin{theorem}[Package governance export sibling independence]
\label{thm:package-governance-export-sibling-independence}
The $\PackageGovernanceExportUp$ carrier is not bijective, under NameCert-row preservation, to $\BedcPhilosophyPackageUp$, $\ClaimRegistryLayerUp$, $\RegistryExportSurfaceUp$, $\AuditExportFirewallUp$, or $\PackageMapBoundaryUp$. Each sibling is consumed through a displayed row, but none carries the joint package, refusal, governance, capstone, export-grade, firewall, target, map-boundary, transport, replay, provenance, and local naming packet.
\end{theorem}
\begin{proof}
Compare the displayed rows. $\BedcPhilosophyPackageUp$ supplies the package ledger, $\ClaimRegistryLayerUp$ supplies claim admission and refusal boundary, $\RegistryExportSurfaceUp$ supplies export rows, $\AuditExportFirewallUp$ supplies same-site audit refusal, and $\PackageMapBoundaryUp$ supplies the theorem, gap, tradition, science, and axis-boundary handoff.

The governance export carrier contains those sibling roles together with the in-place governance row $A$, capstone dependency row $C$, export-grade row $E$, target row $T$, and local NameCert row $N$. A NameCert-row-preserving bijection would have to preserve this joint governance-and-export surface.

No listed sibling has all of these coordinates as local rows. Hence each sibling is a dependency or consumer surface for $\PackageGovernanceExportUp$, not a bijective presentation of it.
\end{proof}

\begin{theorem}[Package governance export capstone dependency exactness]
\label{thm:package-governance-export-capstone-dependency-exactness}
An accepted $\PackageGovernanceExportUp$ packet may expose a capstone export only through the capstone dependency row $C$ together with the map-boundary row $M$ and audit-firewall row $F$. If $C$ omits a displayed dependency family, the packet may still record a package reading, but it cannot certify that reading as a capstone export.
\end{theorem}
\begin{proof}
The capstone row $C$ is the only coordinate that records cross-domain dependencies for a unifying package claim. It must therefore be read before a capstone export grade is projected.

The map-boundary row $M$ then checks that the dependency families are visible as theorem-map, gap-map, tradition-map, scientific-map, and axis-boundary handoffs. The firewall row $F$ checks whether any active refusal or certificate conflict addresses the same site.

If $C$ omits one dependency family, the packet still has package, registry, governance, and export rows. But the capstone-specific dependency certificate is absent, and neither $M$ nor $F$ can manufacture it. The export can remain a package reading or weaker export grade, not a certified capstone export.
\end{proof}

\falsifiablePrediction{Deleting the cannot-claim row or firewall row permits a governance packet to name an export grade without first refusing blocked package readings.}

\independenceWitness{bedcphilosophypackage, claimregistrylayer, registryexportsurface, auditexportfirewall, packagemapboundary: none is bijective because PackageGovernanceExportUp carries the joint governance, capstone-dependency, export-grade, target, firewall, map-boundary, transport, replay, provenance, and local NameCert rows.}

The Lean \texttt{TasteGate.lean} boundary for $\PackageGovernanceExportUp$ must provide $\Nontrivial\ \PackageGovernanceExportUp$ and $\FieldFaithful\ \PackageGovernanceExportUp$ instances in \texttt{lean4/BEDC/Derived/PackageGovernanceExportUp/TasteGate.lean}. The nontriviality witness must expose at least one governed package export decision, and field faithfulness must preserve $P,R,A,C,E,F,T,M,H,K,Q,N$ as distinct rows before any checked marker can cite \texttt{BEDC.Derived.PackageGovernanceExportUp.TasteGate.PackageGovernanceExportTasteGate\_single\_carrier\_alignment}.

\closureat{PackageGovernanceExportUp}{seedStr}

\begin{closurestatus}{\PackageGovernanceExportUp}
  \constructivestory{A $\PackageGovernanceExportUp$ packet is generated from package, cannot-claim registry, in-place governance, capstone dependency, export grade, audit firewall, target route, map-boundary, componentwise transport, displayed replay, package provenance, and local $\NameCert$ rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:package-governance-export-carrier}, \autoref{thm:package-governance-export-namecert-obligations}, \autoref{thm:package-governance-export-refusal-totality}, \autoref{thm:package-governance-export-sibling-independence}, and \autoref{thm:package-governance-export-capstone-dependency-exactness} bind package governance and export to one finite NameCert packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, registry completeness, correctness of every governance action, correctness of every capstone dependency, or whole-package checked export.}
  \upgradepath{Lean closure requires Nontrivial PackageGovernanceExportUp and FieldFaithful PackageGovernanceExportUp instances in \texttt{lean4/BEDC/Derived/PackageGovernanceExportUp/TasteGate.lean}.}
\end{closurestatus}
