\chapter{A Concrete Naming Certificate for $\PhaseGovernedCertificateRouteUp$}
\label{ch:concrete-instances-phasegovernedcertificateroute-namecert}
\origin{ai}

The $\PhaseGovernedCertificateRouteUp$ packet realizes the research-programme route of \autoref{sec:visions-philosophy-research-programme} as a finite certificate router. It sits beside $\ProgrammeStrengthLedgerUp$ of \autoref{ch:concrete-instances-programme-strength-ledger-namecert}, $\PhilosophyCannotClaimRegistryUp$ of \autoref{ch:concrete-instances-philosophy-cannot-claim-registry-namecert}, $\CannotClaimExportGateUp$ of \autoref{ch:concrete-instances-cannot-claim-export-gate-namecert}, and $\UseProcessBoundaryUp$ of \autoref{ch:concrete-instances-use-process-boundary-namecert}: those siblings record strength, refusal, export blocking, and certified-use process boundaries, while this packet binds their rows before a philosophy programme may present a claim as routed through a named certificate phase. The certified-use consumer of \autoref{ch:concrete-instances-certifieduseprocess-namecert} supplies the public use process read by the same route.

\begin{definition}[Phase-governed certificate route carrier]
\label{def:phase-governed-certificate-route-carrier}
A $\PhaseGovernedCertificateRouteUp$ carrier is a finite $\BHist$ packet
$$
R=(A,S,F,E,D,U,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ is the phase row, recording the current certificate phase and the admissible next phase for the programme route;
\item $S$ is the strength row, read from the $\ProgrammeStrengthLedgerUp$ surface;
\item $F$ is the refusal row, read from the $\PhilosophyCannotClaimRegistryUp$ surface;
\item $E$ is the export-gate row, read from the $\CannotClaimExportGateUp$ surface before any checked-target reading is exposed;
\item $D$ is the dependency and failure-audit row, recording open blockers, failed obligations, and audit-facing non-export decisions;
\item $U$ is the certified-use and process-boundary row, read through $\UseProcessBoundaryUp$ and $\CertifiedUseProcessUp$;
\item $H$ records componentwise $\hsame$ transport for phase, strength, refusal, export, dependency, use-process, continuation, provenance, and local naming rows;
\item $C$ records displayed $\Cont$ replay through the same rows;
\item $P$ records $\Pkg$ provenance over $\PhaseGovernedCertificateRouteUp$, $\ProgrammeStrengthLedgerUp$, $\PhilosophyCannotClaimRegistryUp$, $\CannotClaimExportGateUp$, $\UseProcessBoundaryUp$, $\CertifiedUseProcessUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows;
\item $N$ is the local $\NameCert_{\PhaseGovernedCertificateRouteUp}$ row.
\end{enumerate}
The carrier has no coordinate for skipping the phase row, erasing refusal, inflating strength, exporting a blocked target, hiding a failure-audit row, or reading a certified use outside the displayed process boundary.
\end{definition}

\begin{theorem}[Phase-governed certificate route NameCert obligations]
\label{thm:phase-governed-certificate-route-namecert-obligations}
For the carrier of \autoref{def:phase-governed-certificate-route-carrier}, the local $\NameCert_{\PhaseGovernedCertificateRouteUp}$ surface consists exactly of carrier admission for $R=(A,S,F,E,D,U,H,C,P,N)$, phase exposure through $A$, strength exposure through $S$, refusal exposure through $F$, export-gate exposure through $E$, dependency and failure-audit exposure through $D$, certified-use and process-boundary exposure through $U$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the finite packet. The phase row $A$ is read before the strength, refusal, export, dependency, and use-process rows can be treated as one route.

Read the sibling surfaces in the displayed order. The strength ledger supplies $S$, the cannot-claim registry supplies $F$, the export gate supplies $E$, and the use-process boundary supplies $U$; the failure-audit row $D$ records blockers that prevent a stronger certificate reading.

Finally use $H,C,P,N$ to transport, replay, source, and name the same packet. Since no further route coordinate is present, these rows exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Phase-governed certificate route nonescape]
\label{thm:phase-governed-certificate-route-nonescape}
Every accepted $\PhaseGovernedCertificateRouteUp$ consumer reads a programme claim through the phase row $A$, strength row $S$, refusal row $F$, export-gate row $E$, dependency and failure-audit row $D$, certified-use and process-boundary row $U$, transport row $H$, replay row $C$, provenance row $P$, and local naming row $N$. It cannot export a stronger phase, erase a refusal, bypass a blocked export gate, hide a failure-audit row, replace certified use by prose, or obtain a checked target outside those rows.
\end{theorem}
\begin{proof}
Begin with the NameCert obligations. They force any accepted route to expose $A,S,F,E,D,U,H,C,P,N$ before the local name is available.

The sibling packets keep the route non-escaping. $\ProgrammeStrengthLedgerUp$ blocks strength inflation, $\PhilosophyCannotClaimRegistryUp$ preserves the refusal row, $\CannotClaimExportGateUp$ blocks refused checked-target export, and $\UseProcessBoundaryUp$ keeps certified use tied to process mediation.

The remaining transport, replay, provenance, and naming rows preserve that same display. Hence the accepted route has no coordinate from which a stronger phase, erased refusal, bypassed export, hidden blocker, prose-only use, or unchecked target can be exported.
\end{proof}

\falsifiablePrediction{If a PhaseGovernedCertificateRouteUp packet remains accepted after deleting either its phase row or its refusal row, then the route carrier is refuted.}

\independenceWitness{programmestrengthledger, philosophycannotclaimregistry, cannotclaimexportgate, useprocessboundary, certifieduseprocess: none is bijective to PhaseGovernedCertificateRouteUp because the route binds phase, strength, refusal, export gate, failure audit, dependency, certified use, transport, replay, provenance, and local naming in one finite packet.}

The Lean follow-up requires $\Nontrivial\ \PhaseGovernedCertificateRouteUp$ and $\FieldFaithful\ \PhaseGovernedCertificateRouteUp$ instances in \texttt{lean4/BEDC/Derived/PhaseGovernedCertificateRouteUp/TasteGate.lean}. The field-faithfulness witness must keep $A,S,F,E,D,U,H,C,P,N$ as distinct rows before a checked boundary can cite \texttt{BEDC.Derived.PhaseGovernedCertificateRouteUp.TasteGate}.

\closureat{PhaseGovernedCertificateRouteUp}{seedStr}
