\chapter{A Concrete Naming Certificate for $\NestedIntervalIntersectionUp$}
\label{ch:concrete-instances-nestedintervalintersection-namecert}
\origin{human}

The $\NestedIntervalIntersectionUp$ interface names the finite readback surface through which nested interval packets hand a diagonal interval-intersection claim to the real and completion layers. Bishop--Bridges constructive analysis treats nested interval intersection through explicit moduli and finite approximants; BEDC records only the finite diagonal rows, transport ledgers, and seal-facing boundary. It does not claim open-cover compactness, choice of an intersection point, or equality with a host real intersection.

The consumer route enters the L10 real-name chain through the regular Cauchy source surface of \autoref{ch:concrete-instances-regularcauchyname-namecert}; this chapter only adds the nested-interval selector and width-window ledger on top of that sibling carrier.

\begin{definition}[Nested interval intersection carrier]
\label{def:nested-interval-intersection-carrier}
A $\NestedIntervalIntersectionUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
X=(N,W,D,E,H,C,P,Q)
$$
with the following visible coordinates:
\begin{enumerate}
\item $N$ is the source $\NestedIntervalUp$ or $\NestedDyadicIntervalUp$ chain row, including the displayed $\DyadicIntervalUp$ endpoint packets and their $\DyadicRatCoreUp$ lower and upper endpoint reads;
\item $W$ is the displayed width surface, either as explicit width rows for the visible chain or as $\RegularityModulusUp$ rows naming the requested finite precision window;
\item $D$ is the finite diagonal selector: for each displayed precision request, it chooses one visible interval row whose width ledger is bounded by the requested tolerance;
\item $E$ records the selected endpoint enclosures and the finite $\RegSeqRatUp$ handoff rows read from those selected intervals;
\item $H$ is the $\RealUp$ seal-facing surface obtained by routing the selected regular-rational rows through the displayed endpoint and width ledgers;
\item $C$ stores the $\hsame$ and $\Cont$ transports for the source chain, width or modulus rows, diagonal selector, handoff rows, and seal-facing rows;
\item $P$ is the $\Pkg$ provenance naming $\NestedIntervalUp$, $\NestedDyadicIntervalUp$, $\DyadicIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\RegularityModulusUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$ source certificates;
\item $Q$ is the local $\NameCert_{\NestedIntervalIntersectionUp}$ row for the finite intersection readback name.
\end{enumerate}
The carrier predicate is $\mathsf{NestedIntervalIntersectionPacket}(X)$. Its public rows are exactly the displayed source-chain, width, diagonal-selector, endpoint-handoff, seal-facing, transport, package, and local certificate rows.
\end{definition}
\leanchecked{BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionTasteGate\_single\_carrier\_alignment}

\begin{definition}[Nested interval intersection classifier]
\label{def:nested-interval-intersection-classifier}
Two accepted $\NestedIntervalIntersectionUp$ carriers classify together when their source nested-interval rows transport to the same displayed finite window and their diagonal selectors choose endpoint enclosures with the same requested tolerance rows.

Concretely, after the $\hsame$ and $\Cont$ transports recorded in $C$ and $C'$, the classifier compares the selected lower endpoint rows, selected upper endpoint rows, displayed width or $\RegularityModulusUp$ rows, $\RegSeqRatUp$ handoff rows, $\RealUp$ seal-facing rows, $\Pkg$ provenance, and local $\NameCert$ rows componentwise. It does not quotient infinite chains and does not identify a selected point in the intersection.
\end{definition}

\begin{theorem}[Nested interval intersection NameCert obligations]
\label{thm:nested-interval-intersection-namecert-obligations}
The seed $\NameCert_{\NestedIntervalIntersectionUp}$ surface has five obligations:
\begin{enumerate}
\item carrier: formation of the finite $\mathsf{BHist}$ packet of \autoref{def:nested-interval-intersection-carrier};
\item classifier: the finite-window classifier of \autoref{def:nested-interval-intersection-classifier};
\item diagonal stability: the selected interval row remains accepted when the source $\NestedIntervalUp$ or $\NestedDyadicIntervalUp$ chain, width or $\RegularityModulusUp$ row, and endpoint packets are transported through the displayed $\hsame$ and $\Cont$ routes;
\item handoff exactness: every $\RegSeqRatUp$ row read by the carrier is one of the endpoint enclosures selected by the finite diagonal selector;
\item seal boundary: the $\RealUp$ surface consumes only the selected finite regular-rational rows, package provenance, and local certificate row.
\end{enumerate}
These obligations are the complete seed certificate surface for finite nested-interval intersection readback.
\end{theorem}
\begin{proof}
Carrier formation is the assembly of the displayed packet. The source chain is already supplied by $\NestedIntervalUp$ or $\NestedDyadicIntervalUp$, the endpoint packets are $\DyadicIntervalUp$ rows, and the selected endpoint reads are $\DyadicRatCoreUp$ rows attached to the same finite history.

The classifier is finite because each comparison is made at the requested displayed precision window. After transporting both packets to that window, the selected lower endpoints, selected upper endpoints, width or modulus rows, handoff rows, seal-facing rows, provenance rows, and local certificate rows are compared component by component.

Diagonal stability follows by transporting the source chain and the width surface first, then reading the same requested tolerance row through the transported selector. Since the selector chooses only from displayed intervals, the transported selected row remains a visible row of the transported chain.

Handoff exactness is a projection from the coordinate $E$: every regular-rational read is attached to one selected endpoint enclosure. The seal boundary is a projection from $H$, which routes those same finite rows to $\RealUp$ without adding an infinite chain, compactness principle, choice operator, or host real equality.
\end{proof}
\leanchecked{BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_namecert\_obligations}

\begin{theorem}[Nested interval intersection finite diagonal handoff]
\label{thm:nested-interval-intersection-finite-diagonal-handoff}
For every accepted $\NestedIntervalIntersectionUp$ carrier and every displayed precision request, the consumer-visible $\RegSeqRatUp$ read factors through exactly one selected finite interval row of the source $\NestedIntervalUp$ or $\NestedDyadicIntervalUp$ chain, its $\DyadicIntervalUp$ endpoint packet, its lower and upper $\DyadicRatCoreUp$ rows, and the displayed width or $\RegularityModulusUp$ witness that justifies the request.

The handoff exports no completed intersection point, no hidden tail of the chain, and no host completeness datum.
\end{theorem}
\begin{proof}
Project the selector coordinate $D$ from \autoref{def:nested-interval-intersection-carrier}. A precision request is answered by a visible interval row together with its displayed width or regularity-modulus witness.

Read the selected interval through the source chain coordinate $N$. Its lower and upper endpoints are the $\DyadicRatCoreUp$ rows of the selected $\DyadicIntervalUp$ packet, and the width or modulus row is the only bound supplied to the consumer at that request.

Now project the handoff coordinate $E$. The $\RegSeqRatUp$ row is obtained by repacking the selected finite endpoint enclosure and the displayed bound. Since $E$ has no coordinate for an infinite tail or a completed point, every consumer read factors through the selected finite interval row just described.
\end{proof}
\leanchecked{BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_finite\_diagonal\_handoff}

\begin{theorem}[Nested interval intersection selector transport determinacy]
\label{thm:nested-interval-intersection-selector-transport-determinacy}
If two accepted $\NestedIntervalIntersectionUp$ carriers classify together,
their transported diagonal selectors choose the same visible interval row at
each displayed precision window. Hence the selected endpoint packets, the
displayed width or $\RegularityModulusUp$ row, the $\RegSeqRatUp$ handoff, and
the $\RealUp$ seal-facing row are determined by classifier-visible data.

In particular, selector transport cannot exchange the finite diagonal row for
an unrecorded chain tail, a chosen intersection point, host real equality, or
an ambient completeness witness.
\end{theorem}
\leanchecked{BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_selector\_transport\_determinacy}
\begin{proof}
Use the classifier definition to transport both carriers to the same displayed
precision window. At that window, the source chain rows, endpoint packets,
width or modulus rows, handoff rows, seal-facing rows, package provenance, and
local certificate rows are compared componentwise.

Project the selector coordinate $D$ from each transported carrier. Since the
classifier compares the selected endpoint enclosures at the same requested
tolerance, both selectors point to the same visible interval row of the
transported finite window.

Apply
\autoref{thm:nested-interval-intersection-finite-diagonal-handoff} to that
selected row. The consumer-visible $\RegSeqRatUp$ handoff is then forced to
factor through the same endpoint packet and the same displayed width or
regularity-modulus witness.

The seal-facing coordinate is read from this handoff and the displayed
transports. No remaining carrier coordinate contains a hidden chain tail,
chosen intersection element, host equality row, or completeness datum.
\end{proof}

\begin{theorem}[Nested interval intersection real seal boundary]
\label{thm:nested-interval-intersection-real-seal-boundary}
The $\RealUp$-facing boundary of an accepted $\NestedIntervalIntersectionUp$ carrier is exactly the finite diagonal handoff surface of \autoref{thm:nested-interval-intersection-finite-diagonal-handoff}, together with the displayed $\hsame$ transports, visible $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert_{\NestedIntervalIntersectionUp}$ row.

In particular, the boundary does not assert Cantor nested-interval convergence, open-cover compactness, extraction of a point by choice, uniqueness of an intersection element, or equality with a host real value.
\end{theorem}
\begin{proof}
Start with the seal-facing coordinate $H$ in \autoref{def:nested-interval-intersection-carrier}. Its inputs are the selected regular-rational rows from $E$, the transports in $C$, the package provenance $P$, and the local certificate row $Q$.

Use \autoref{thm:nested-interval-intersection-finite-diagonal-handoff} to identify the regular-rational inputs. Each such input has already factored through one visible interval row, its endpoint packet, and its displayed width or modulus witness.

The remaining coordinates are bookkeeping rows: $\hsame$ transports, $\Cont$ routes, $\Pkg$ provenance, and the local naming certificate. None of them contains a compactness theorem, a point-selection operator, a uniqueness claim, or a host real equality row. Therefore the real-seal boundary is precisely the finite surface stated above.
\end{proof}

\begin{theorem}[Nested interval dyadic selector coverage]
\label{thm:nested-interval-dyadic-selector-coverage}
Every $\RealUp$-facing consumer read of an accepted $\NestedIntervalIntersectionUp$ packet is covered by one selected finite interval row. The selected row has lower and upper endpoint reads in $\DyadicRatCoreUp$, its displayed width or $\RegularityModulusUp$ row supplies the requested $\RegSeqRatUp$ handoff, and its provenance is exactly the recorded $\Pkg$ and local $\NameCert_{\NestedIntervalIntersectionUp}$ route transported through the visible $\hsame$ and $\Cont$ rows.

Consequently a diagonal-limit or completion consumer reads a dyadic endpoint enclosure selected by the finite selector, not a hidden chain tail, a chosen intersection point, or an ambient compactness witness.
\end{theorem}
\begin{proof}
Begin with the consumer-visible regular-rational read. By \autoref{thm:nested-interval-intersection-finite-diagonal-handoff}, the read factors through exactly one visible interval row of the source chain, its endpoint packet, its lower and upper dyadic endpoint rows, and its displayed width or modulus witness.

Transport the selector data next. The determinacy result \autoref{thm:nested-interval-intersection-selector-transport-determinacy} says that classified packets choose the same visible row at the same precision window, so the lower endpoint, upper endpoint, width row, and $\RegSeqRatUp$ handoff remain tied to that selected interval.

Finally apply \autoref{thm:nested-interval-intersection-real-seal-boundary}. The $\RealUp$ boundary adds only the displayed $\hsame$ rows, $\Cont$ routes, $\Pkg$ provenance, and local naming row to the finite diagonal handoff.

The carrier has no coordinate for a completed point, open-cover compactness, choice, or host real equality. Hence every $\RealUp$-facing read is covered by the selected dyadic endpoint row and its recorded provenance.
\end{proof}

\begin{theorem}[Nested interval intersection width-window refinement]
\label{thm:nested-interval-intersection-width-window-refinement}
For any accepted $\NestedIntervalIntersectionUp$ carrier
$$
X=(N,W,D,E,H,C,P,Q),
$$
every consumer precision request refines through one displayed width row or $\RegularityModulusUp$ row $W$, one selected interval row from the diagonal selector $D$, its $\DyadicIntervalUp$ endpoint packet, the $\RegSeqRatUp$ handoff row $E$, and the $\RealUp$ seal boundary $H$. This refinement is transported only by the displayed $\hsame$ and $\Cont$ rows recorded in $C$, together with the package provenance $P$ and local $\NameCert_{\NestedIntervalIntersectionUp}$ row $Q$.

Thus the width-window row is the exact finite surface consumed by diagonal-limit and completion-facing handoffs; it is not a claim of a chosen intersection point, open-cover compactness, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:nested-interval-intersection-finite-diagonal-handoff}. It identifies the consumer-visible $\RegSeqRatUp$ read with one selected interval row, its endpoint packet, and the displayed width or regularity-modulus witness for the requested precision.

Next apply \autoref{thm:nested-interval-intersection-selector-transport-determinacy}. The selected interval row remains determined after the $\hsame$ and $\Cont$ transports, so the endpoint packet and width-window witness cannot be exchanged for an unrecorded chain tail.

Use \autoref{thm:nested-interval-intersection-real-seal-boundary} to route the handoff into the $\RealUp$ surface. The seal sees the same finite diagonal package plus the displayed transports, provenance, and local naming row.

Finally \autoref{thm:nested-interval-dyadic-selector-coverage} covers every $\RealUp$-facing consumer read by the selected dyadic endpoint row. Therefore the width-window refinement is the reusable finite surface for the diagonal handoff.
\end{proof}

\begin{theorem}[Nested interval intersection width-tail Cauchy handoff]
\label{thm:nested-interval-intersection-width-tail-cauchy-handoff}
Let
$$
X=(N,W,D,E,H,C,P,Q)
$$
be an accepted $\NestedIntervalIntersectionUp$ carrier. If the displayed width rows or $\RegularityModulusUp$ rows in $W$ are cofinal for the requested tolerance schedule, then the selected endpoint enclosures determined by the diagonal selector $D$ form a $\RegSeqRatUp$-compatible Cauchy handoff consumed by the same $\RealUp$ seal boundary $H$.

This handoff is carried only by the source chain $N$, the width or regularity ledger $W$, the finite selector $D$, the endpoint handoff rows $E$, the seal boundary $H$, the displayed transports $C$, the package provenance $P$, and the local $\NameCert_{\NestedIntervalIntersectionUp}$ row $Q$. It asserts no chosen intersection point, open-cover compactness, host real equality, or ambient completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:nested-interval-intersection-finite-diagonal-handoff}. It identifies each requested precision with one selected interval row, its endpoint packet, and the displayed width or regularity witness.

Use \autoref{thm:nested-interval-intersection-selector-transport-determinacy} to keep the selected endpoint enclosures fixed under the displayed transports. The selector therefore supplies one transported endpoint enclosure for each requested tolerance window.

Apply \autoref{thm:nested-interval-dyadic-selector-coverage} and \autoref{thm:nested-interval-intersection-width-window-refinement}. Cofinality of the width or regularity rows makes the selected endpoint enclosures compatible with the requested Cauchy tolerance schedule, so the handoff is a $\RegSeqRatUp$-compatible tail surface.

Finally route the handoff through \autoref{thm:nested-interval-intersection-real-seal-boundary}. The $\RealUp$ seal reads the same finite endpoint, width, transport, package, and local certificate rows, and the carrier has no coordinate for point extraction, compactness, host equality, or ambient completeness.
\end{proof}

\closureat{NestedIntervalIntersectionUp}{seedStr}
\closureat{NestedIntervalIntersectionUp}{obligationStr}[BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_namecert\_obligations]
\closureat{NestedIntervalIntersectionUp}{scopedStr}[BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_namecert\_obligations]

\begin{closurestatus}{\NestedIntervalIntersectionUp}
  \constructivestory{A $\NestedIntervalIntersectionUp$ packet is generated from a finite $\NestedIntervalUp$ or $\NestedDyadicIntervalUp$ chain, displayed $\DyadicIntervalUp$ endpoint packets, $\DyadicRatCoreUp$ endpoint reads, width or $\RegularityModulusUp$ rows, a finite diagonal selector, $\RegSeqRatUp$ handoff rows, a $\RealUp$ seal-facing surface, displayed $\hsame$ and $\Cont$ transports, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The seed scope registers the carrier, finite-window classifier, five-row naming-certificate obligation surface, finite diagonal handoff, and real-seal boundary for nested interval intersection readback over $\NestedIntervalUp$, $\NestedDyadicIntervalUp$, $\DyadicIntervalUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, and $\RegularityModulusUp$.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.NestedIntervalIntersectionUp.NestedIntervalIntersectionCarrier\_namecert\_obligations}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close Cantor nested-interval convergence, open-cover compactness, point extraction, uniqueness of an intersection element, or host real equality.}
  \upgradepath{The next paper grade is a public export theorem for the finite diagonal intersection surface.}
\end{closurestatus}
