\chapter{A Concrete Naming Certificate for $\UniformContinuityUp$}
\label{ch:concrete-instances-uniformcontinuity-namecert}
\origin{human}

The $\UniformContinuityUp$ surface materializes the compact-uniform-continuity
capstone of \autoref{ch:visions-compact-uniform-continuity} as an ordinary
concrete instance. It consumes the finite-net certificate of $\CompactUp$, the
located distance rows of $\MetricUp$, the pointwise modulus ledger of
$\ContinuousUp$, the rational lower-bound ledger of $\RatUp$, and the closed
$\mathsf{ProbeBundle}$ spine. The exported object is a tolerance-only
uniform-modulus certificate; it is not a host-level modulus selector.

The dependency rows are read from sibling concrete certificates: the finite-net
row from \autoref{ch:concrete-instances-compact-namecert}, the source and
target distance rows from \autoref{ch:concrete-instances-metric-namecert}, the
pointwise graph and modulus rows from
\autoref{ch:concrete-instances-continuous-namecert}, and the lower-bound
ledger from \autoref{ch:concrete-instances-rat-namecert}.

\begin{definition}[UniformContinuity BHist carrier]
\label{def:uniform-continuity-bhist-carrier}
A $\UniformContinuityUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
U=(X,Y,f,\varepsilon,P,C,R,T,L,M,H,N)
$$
with the following visible rows:
\begin{enumerate}
\item $X$ is the source metric row consumed through $\NameCert_{\MetricUp}$;
\item $Y$ is the target metric row consumed through $\NameCert_{\MetricUp}$;
\item $f$ is the graph row consumed through $\NameCert_{\ContinuousUp}$;
\item $\varepsilon$ is a positive tolerance row consumed through $\NameCert_{\RatUp}$;
\item $P$ is the finite $\mathsf{ProbeBundle}$ row supplied by the compact certificate;
\item $C$ lists the center histories indexed by the bundled probes;
\item $R$ lists the local positive radius and pointwise precision histories;
\item $T$ records the half-radius coverage rows from $\NameCert_{\CompactUp}$;
\item $L$ records the $\RatUp$ lower-bound fold over the bundled radius rows;
\item $M$ records the metric triangle transports in the source and target metrics;
\item $H$ records $\hsame$ transport for the displayed histories;
\item $N$ is the local $\NameCert_{\UniformContinuityUp}$ row.
\end{enumerate}
The packet is accepted only when these rows are tied by $\Cont$ routes and
$\mathsf{Pkg}$ provenance to the listed dependency certificates. No coordinate
stores a function from tolerances to radii outside $\mathsf{BHist}$.
\end{definition}
\leandef{BEDC.Derived.UniformContinuityUp.UniformContinuityCarrier}

\begin{definition}[UniformContinuity classifier]
\label{def:uniform-continuity-classifier}
Two $\UniformContinuityUp$ packets
$$
U=(X,Y,f,\varepsilon,P,C,R,T,L,M,H,N)
$$
and
$$
U'=(X',Y',f',\varepsilon',P',C',R',T',L',M',H',N')
$$
are classified together when the source and target metric rows are transported
by their $\MetricUp$ classifiers, the graph row is transported by the
$\ContinuousUp$ classifier, the tolerance and folded precision rows are
transported by the $\RatUp$ classifier, the $\mathsf{ProbeBundle}$ membership
spine is the same displayed finite spine after $\hsame$ transport, and the
coverage, pointwise-modulus, lower-bound, and triangle rows are the
corresponding transported rows. The classifier compares exactly the displayed
certificate packet and does not compare host functions, external compact
covers, or selected moduli.
\end{definition}
\leanchecked{BEDC.Derived.UniformContinuityUp.TasteGate.UniformContinuityTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Finite-net modulus fold]
\label{thm:uniform-continuity-finite-net-modulus-fold}
Let $U$ be an accepted $\UniformContinuityUp$ carrier. The finite
$\mathsf{ProbeBundle}$ row $P$, the pointwise-modulus rows $R$, and the
$\RatUp$ lower-bound ledger $L$ determine a folded positive precision history
$\delta_\varepsilon$ such that, for every bundled probe $p$, the fold certifies
$\delta_\varepsilon$ below the half-radius row attached to $p$. The same
folded history is stable under the classifier of
\autoref{def:uniform-continuity-classifier}. Therefore the uniform precision
read by a consumer is a BEDC history extracted from the finite bundle, not an
external selection.
\end{theorem}
\leanchecked{BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_finite\_net\_modulus\_fold}
\begin{proof}
Project the finite $\mathsf{ProbeBundle}$ spine from the carrier. Its center
rows, local radius rows, and pointwise precision rows are displayed
coordinates of $U$, and each row is attached to the compact and continuous
dependency certificates by $\Cont$ and $\mathsf{Pkg}$ provenance.

Run primitive recursion over the bundle. At the empty boundary the accepted
carrier supplies the nonempty compact-net witness, so the fold starts from a
displayed positive radius row. At each successor probe, the $\RatUp$ comparison
row selects the certified lower of the accumulator and the next half-radius
row, and stores the selected row back in $L$.

Classifier stability follows coordinatewise. Transporting $U$ to $U'$ moves
the rational rows through the $\RatUp$ classifier and moves the bundle
membership witnesses through the same displayed finite spine. The recursion
therefore reads the transported lower-bound ledger, so the folded precision
history is classified with its transported representative.
\end{proof}
\leanchecked{BEDC.Derived.UniformContinuityUp.UniformContinuityCarrier\_finite\_net\_modulus\_fold}

\begin{theorem}[UniformContinuity NameCert obligation surface]
\label{thm:uniform-continuity-namecert-obligation-surface}
The local $\NameCert_{\UniformContinuityUp}$ obligation surface consists
exactly of the following five rows:
\begin{enumerate}
\item the finite-net carrier row exposing the compact $\mathsf{ProbeBundle}$,
its center histories, and half-radius coverage witnesses;
\item the pointwise-to-uniform modulus fold row of
\autoref{thm:uniform-continuity-finite-net-modulus-fold};
\item the $\RatUp$ lower-bound ledger certifying the folded positive precision
below every bundled half-radius row;
\item the metric triangle transport row carrying the source estimate through a
chosen center and then carrying the two target estimates to the final
$\varepsilon$ bound;
\item the non-escape row saying that every consumer-visible modulus read
factors through the displayed compact, continuous, rational, metric,
$\mathsf{ProbeBundle}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and local
$\NameCert_{\UniformContinuityUp}$ rows.
\end{enumerate}
Consequently the public certificate exports a tolerance-only
uniform-modulus ledger and exports no host-level modulus selector, no
unlisted open cover, no sequential compactness argument, and no chosen
subsequence.
\end{theorem}
\leanchecked{BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_namecert\_obligation\_surface}
\begin{proof}
The finite-net row is the compact certificate projected to the displayed
$\mathsf{ProbeBundle}$, center histories, and half-radius coverage witnesses.
Those rows are already part of the carrier, so the local packet has no hidden
cover coordinate.

The pointwise-to-uniform row is the finite fold of
\autoref{thm:uniform-continuity-finite-net-modulus-fold}. Its output is a
positive $\RatUp$ history below every bundled half-radius row, and the
classifier stability of that theorem gives the corresponding transport field
for the local $\NameCert$ packet.

The metric row applies the source triangle inequality around the selected
center, then applies the target triangle inequality to the two pointwise
estimates produced by the continuous certificate. The rational ledger supplies
the displayed comparison rows needed to keep the source distances inside the
local pointwise radii.

Finally inspect the carrier coordinates of
\autoref{def:uniform-continuity-bhist-carrier}. They list all dependency
certificates, all finite bundle rows, all rational comparison rows, all metric
transport rows, and the local naming row. A consumer-visible read must factor
through one of these coordinates, so there is no readable slot for an external
modulus selector, sequential compactness witness, or host cover.
\end{proof}

\begin{theorem}[Compact continuous standard reading]
\label{thm:uniform-continuity-compact-continuous-standard-reading}
When a classical compact metric source and a continuous graph are presented
through $\NameCert_{\CompactUp}$, $\NameCert_{\MetricUp}$, and
$\NameCert_{\ContinuousUp}$, the accepted $\UniformContinuityUp$ packet reads
as the usual statement that a continuous function on a compact metric space is
uniformly continuous. The BEDC reading is the finite certificate surface:
for each positive $\RatUp$ tolerance history $\varepsilon$, the packet returns
a folded positive $\RatUp$ precision history $\delta_\varepsilon$ whose
validity is witnessed by finite-net coverage, pointwise continuity at bundled
centers, rational lower-bound comparison, and metric triangle transport.
\end{theorem}
\leanchecked{BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_compact\_continuous\_standard\_reading}
\begin{proof}
Start with the compact certificate. It supplies the finite
$\mathsf{ProbeBundle}$ net and the half-radius coverage witnesses for the
chosen tolerance scale. The continuous certificate supplies pointwise modulus
rows at the bundled centers.

Apply \autoref{thm:uniform-continuity-finite-net-modulus-fold} to extract the
single folded precision history. The fold uses only the displayed rational
ledger and is stable under the packet classifier, so it is the public precision
read by $\NameCert_{\UniformContinuityUp}$.

For any two accepted source histories whose source distance is below this
precision, choose the covering bundled center for the first history. The source
triangle row places the second history within the same local pointwise radius,
and the target triangle row combines the two pointwise estimates into the
displayed tolerance bound. This is precisely the classical Heine--Cantor
reading, expressed through finite BEDC certificate rows.
\end{proof}

\begin{theorem}[UniformContinuity modulus non-escape]
\label{thm:uniform-continuity-modulus-non-escape}
Every consumer-visible modulus row of an accepted $\UniformContinuityUp$
packet factors through the compact $\mathsf{ProbeBundle}$ row, the
$\ContinuousUp$ pointwise rows, the $\RatUp$ lower-bound ledger, the
$\MetricUp$ triangle rows, and the local $\NameCert_{\UniformContinuityUp}$
row of \autoref{def:uniform-continuity-bhist-carrier}, with the folded
precision supplied by \autoref{thm:uniform-continuity-finite-net-modulus-fold}.
The packet exports no host function from tolerances to radii, no open-cover
selection, no sequential compactness witness, and no choice-selected center.
\end{theorem}
\leanchecked{BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_modulus\_non\_escape}
\begin{proof}
Project the carrier coordinates of
\autoref{def:uniform-continuity-bhist-carrier}. The only modulus-facing data
are the compact $\mathsf{ProbeBundle}$ row $P$, the center and pointwise rows
$C$ and $R$, the compact coverage row $T$, the rational lower-bound ledger
$L$, the metric triangle row $M$, and the local naming row $N$.

Apply the finite-net fold of
\autoref{thm:uniform-continuity-finite-net-modulus-fold}. It constructs the
folded precision from the displayed bundle, pointwise rows, and rational
ledger, and its classifier stability keeps that folded row inside the same
transported packet.

The obligation surface of
\autoref{thm:uniform-continuity-namecert-obligation-surface} identifies this
folded row as the local consumer-visible modulus route. The metric rows then
use exactly the displayed triangle transports to turn the folded source
precision into the target tolerance estimate.

Inspecting the carrier shape completes the non-escape claim. No coordinate
stores a host tolerance-to-radius function, an open-cover selector, a
sequential compactness witness, or a choice-selected center, so none of those
objects can be exported by a modulus read.
\end{proof}

\closureat{UniformContinuityUp}{seedStr}
\closureat{UniformContinuityUp}{obligationStr}[BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_namecert\_obligation\_surface]
\closureat{UniformContinuityUp}{scopedStr}[BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_namecert\_obligation\_surface]
\closureat{UniformContinuityUp}{publicStr}
\closureat{UniformContinuityUp}{bridgedStr}[BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_compact\_continuous\_standard\_reading]
\closureat{UniformContinuityUp}{matureStr}[BEDC.Derived.UniformContinuityUp.UniformContinuityPacket\_compact\_continuous\_standard\_reading]

\begin{closurestatus}{\UniformContinuityUp}
  \constructivestory{A $\UniformContinuityUp$ packet is generated from $\CompactUp$, $\MetricUp$, $\ContinuousUp$, $\RatUp$, $\mathsf{ProbeBundle}$, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ rows that display finite-net coverage, pointwise control, rational lower bounds, metric triangle routing, and modulus readback.}
  \theoryclosure{\matureClosure}
  \scopeclosed{The public surface is the compact-continuous modulus export binding the compact $\mathsf{ProbeBundle}$, $\ContinuousUp$ pointwise rows, $\RatUp$ lower-bound ledger, $\MetricUp$ triangle rows, $\hsame$, $\Cont$, $\Pkg$, and local $\NameCert$ dependencies for the displayed finite-net modulus packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close host modulus selectors, open-cover compactness, sequential compactness, choice-selected centers, or bridge checking.}
  \upgradepath{No further paper-side theory-closure upgrade remains; formal and bridge checking remain separate axes.}
\end{closurestatus}
