\chapter{A Concrete Naming Certificate for $\EpistemicOntologyBridgeUp$}
\label{ch:concrete-instances-epistemicontologybridge-namecert}
\origin{ai}

The $\EpistemicOntologyBridgeUp$ packet realizes the philosophy total-synthesis surface of \autoref{sec:visions-philosophy-total-synthesis} as a finite bridge between objecthood, knowledge licensing, observation logic, phenomenology-science interface data, audit export, and local naming. It sits beside the firewall of \autoref{ch:concrete-instances-auditexportfirewall-namecert}, the object-knowledge certificate of \autoref{ch:concrete-instances-objectknowledgecertificate-namecert}, the observation-logic boundary of \autoref{ch:concrete-instances-observation-logic-boundary-namecert}, and the phenomenology-science interface of \autoref{ch:concrete-instances-phenomenology-science-interface-namecert}. Those siblings expose export refusal, object-witness evidence, observation admissibility, and phenomenology-to-science handoff separately; this bridge binds their rows before a public synthesis read may treat ontology and epistemology as one certified surface.

\begin{definition}[Epistemic ontology bridge carrier]
\label{def:epistemic-ontology-bridge-carrier}
An $\EpistemicOntologyBridgeUp$ carrier is a finite $\BHist$ packet
$$
E=(O,K,Q,P,A,L,H,C,R,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $O$ is the ontology row, recording the finite objecthood and constitution data read from $\ObjectKnowledgeCertificateUp$.
\item $K$ is the epistemology row, recording the knowledge-license and witness-admissibility data attached to the same object site.
\item $Q$ is the observation-logic row, recording admissible observation claims from $\ObservationLogicBoundaryUp$.
\item $P$ is the phenomenology-science row, recording the interface route from phenomenal framing to public scientific inscription.
\item $A$ is the audit-export row, recording the firewall decision from $\AuditExportFirewallUp$.
\item $L$ is the bridge ledger row, recording that $O,K,Q,P,A$ are read in one public synthesis packet.
\item $H$ records componentwise $\hsame$ transport for the ontology, epistemology, observation-logic, phenomenology-science, audit-export, ledger, replay, provenance, and local naming rows.
\item $C$ records displayed $\Cont$ replay for the same bridge packet.
\item $R$ is the $\Pkg$ provenance over $\EpistemicOntologyBridgeUp$, $\ObjectKnowledgeCertificateUp$, $\ObservationLogicBoundaryUp$, $\PhenomenologyScienceInterfaceUp$, $\AuditExportFirewallUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\EpistemicOntologyBridgeUp}$ row.
\end{enumerate}
The carrier has no coordinate for ontology without witness, epistemology without object row, observation outside the observation-logic boundary, phenomenology without science-interface handoff, audit export without firewall decision, or host-level synthesis truth.
\end{definition}
\leanchecked{BEDC.Derived.EpistemicOntologyBridgeUp.EpistemicOntologyBridgeTasteGate\_single\_carrier\_alignment}

\begin{definition}[Epistemic ontology bridge classifier]
\label{def:epistemic-ontology-bridge-classifier}
The classifier for $\EpistemicOntologyBridgeUp$ accepts exactly those packets $E=(O,K,Q,P,A,L,H,C,R,N)$ whose ontology row $O$, epistemology row $K$, observation-logic row $Q$, phenomenology-science row $P$, audit-export row $A$, bridge ledger row $L$, transport row $H$, replay row $C$, provenance row $R$, and local name row $N$ are all displayed in the same finite $\BHist$ carrier and preserved by the local $\NameCert_{\EpistemicOntologyBridgeUp}$ row. It rejects any packet that omits one of those rows or replaces the bridge by a host-side identification of being, knowing, observing, experiencing, and exporting.
\end{definition}

\begin{theorem}[Epistemic ontology bridge NameCert obligations]
\label{thm:epistemic-ontology-bridge-namecert-obligations}
For the carrier of \autoref{def:epistemic-ontology-bridge-carrier} and classifier of \autoref{def:epistemic-ontology-bridge-classifier}, the local $\NameCert_{\EpistemicOntologyBridgeUp}$ surface consists exactly of five obligations:
\begin{enumerate}
\item carrier admission for the displayed packet $E=(O,K,Q,P,A,L,H,C,R,N)$;
\item classifier exactness for accepting exactly the same displayed packet and rejecting host-side synthesis replacements;
\item cross-face preservation for ontology, epistemology, observation-logic, phenomenology-science, audit-export, and bridge-ledger rows;
\item structural preservation by componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, and $\Pkg$ provenance through $R$;
\item local naming through $N$ with no unlicensed ontology, objectless knowledge, unbounded observation claim, unbridged phenomenology, firewall bypass, or host-level synthesis truth row.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:epistemic-ontology-bridge-carrier}. The rows $O,K,Q,P,A,L$ are the only cross-face data coordinates available before transport, replay, provenance, and local naming are read.

Read the classifier of \autoref{def:epistemic-ontology-bridge-classifier}. Its accepted packet is the same displayed tuple, so carrier admission and classifier exactness have the same finite boundary.

Inspect the sibling rows. The object-knowledge row supplies ontology and epistemology evidence, the observation-logic row supplies admissible observation form, the phenomenology-science row supplies public interface transport, and the audit-export row supplies the firewall boundary.

Finally inspect $H,C,R,N$. These rows preserve, replay, source, and name the same packet, so the bridge cannot add a hidden synthesis coordinate outside the displayed carrier. The listed rows therefore exhaust the local NameCert obligations.
\end{proof}

\begin{theorem}[Epistemic ontology bridge audit-export boundary]
\label{thm:epistemic-ontology-bridge-audit-export-boundary}
If any ontology, epistemology, observation-logic, phenomenology-science, audit-export, bridge-ledger, transport, replay, provenance, or local naming row is absent from an $\EpistemicOntologyBridgeUp$ packet, then the classifier rejects the public export. In particular, the bridge cannot turn an object row alone, a knowledge row alone, an observation row alone, a phenomenology-science handoff alone, or a firewall decision alone into a total philosophy synthesis.
\end{theorem}
\begin{proof}
Start from \autoref{def:epistemic-ontology-bridge-classifier}. Acceptance requires the displayed rows $O,K,Q,P,A,L,H,C,R,N$ in one finite carrier.

Apply \autoref{thm:epistemic-ontology-bridge-namecert-obligations}. The local NameCert obligations preserve each cross-face row before any public export may consume the packet.

If one row is absent, the classifier has no projection for the corresponding face or structural support. The audit-export row $A$ therefore remains a firewall decision inside the packet rather than a replacement for the missing ontology, epistemology, observation-logic, phenomenology-science, ledger, transport, replay, provenance, or local name row.
\end{proof}

\falsifiablePrediction{If any ontology, epistemology, observation-logic, phenomenology-science, or audit-export row is absent, the bridge classifier rejects the public export.}

\independenceWitness{auditexportfirewall, objectknowledgecertificate, observationlogicboundary, phenomenologyscienceinterface: each sibling supplies one face or firewall boundary, while EpistemicOntologyBridgeUp binds the cross-face bridge; no bijection preserves all rows.}

Lean \texttt{TasteGate.lean} for this route must provide \texttt{Nontrivial EpistemicOntologyBridgeUp} and \texttt{FieldFaithful EpistemicOntologyBridgeUp} instances in \texttt{BEDC.Derived.EpistemicOntologyBridgeUp}.

\closureat{EpistemicOntologyBridgeUp}{seedStr}

\begin{closurestatus}{\EpistemicOntologyBridgeUp}
  \constructivestory{An $\EpistemicOntologyBridgeUp$ packet is generated from finite ontology, epistemology, observation-logic, phenomenology-science, audit-export, ledger, transport, replay, provenance, and local NameCert rows.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:epistemic-ontology-bridge-carrier}, \autoref{def:epistemic-ontology-bridge-classifier}, \autoref{thm:epistemic-ontology-bridge-namecert-obligations}, and \autoref{thm:epistemic-ontology-bridge-audit-export-boundary} bind the bridge carrier, classifier, NameCert obligations, and export boundary as a finite synthesis surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a Lean implementation, checked bridge status, host-level synthesis truth, ontology without witness, objectless knowledge, observation outside the observation-logic boundary, unbridged phenomenology, or firewall bypass.}
  \upgradepath{The next paper-side step is public export after Lean encoding catches up to the carrier, classifier, NameCert obligations, and audit-export boundary.}
\end{closurestatus}
