\chapter{A Concrete Naming Certificate for $\InfCatUp$}
\label{ch:concrete-instances-infcat-namecert}

The $\infty$-category interface $\InfCatUp$ packages a simplicial-set carrier satisfying the inner-horn lifting condition (a quasicategory). It depends on $\NameCert_{\SimplicialSetUp}$ (\autoref{ch:concrete-instances-simplicialset-namecert}) and $\NameCert_{\CategoryUp}$ (\autoref{ch:concrete-instances-category-namecert}).

\section{Carrier definition}
\label{sec:infcat-carrier}

\begin{definition}[InfCatUp BHist source packet]
\label{def:infcat-bhist-source-packet}
An $\InfCatUp$ $\mathsf{BHist}$ source packet is a finite tuple
$$
\mathcal{I}=(S,C,H,L,\rho,\lambda)
$$
whose coordinates are all displayed BEDC rows. The row $S$ is the consumed
$\NameCert_{\SimplicialSetUp}$ row, carrying the simplicial carrier, face and
degeneracy rows, and the simplicial classifier surface. The row $C$ is the
consumed $\NameCert_{\CategoryUp}$ row used for ordinary categorical source
faces read by downstream consumers.

The row $H$ is the inner-horn ledger. It records finite horn-boundary rows,
the missing inner face, the displayed filler endpoint, and the $\hsame$
comparisons that identify the filler boundary with the named horn boundary
inside the simplicial-set carrier $S$. The row $L$ is the lifting-witness
ledger: each lifting entry is a finite $\mathsf{ProbeBundle}$ row whose source
and target faces are read through $S$, whose ordinary categorical endpoint is
read through $C$ when present, and whose continuation endpoint is recorded by
$\Cont$.

The row $\rho$ is the $\Pkg$ provenance row for the consumed simplicial-set
and category certificates, the horn ledger, and the lifting ledger. The row
$\lambda$ is the $\Cont/\hsame$ transport ledger comparing the simplicial
faces, horn boundaries, fillers, lifting witnesses, and provenance entries
under rowwise replacement. The packet has no coordinate for a host
quasicategory, a localization, or a simplicial mapping object.
\end{definition}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_provenance\_transport\_spine}

\section{The certificate}
\label{sec:infcat-certificate}

\begin{theorem}[InfCatUp obligation inventory fields]
\label{thm:infcat-obligation-inventory-fields}
Every accepted $\InfCatUp$ $\mathsf{BHist}$ source packet contains exactly the
displayed inventory needed by the next obligation layer: the consumed
$\NameCert_{\SimplicialSetUp}$ row, the consumed $\NameCert_{\CategoryUp}$ row,
the finite inner-horn ledger, the lifting ledger, the $\mathsf{ProbeBundle}$
rows supporting the lifting entries, the $\Cont$ transport rows, the $\hsame$
comparison rows, and the $\Pkg$ provenance fields.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_obligation\_inventory\_fields}
\begin{proof}
Unfold \autoref{def:infcat-bhist-source-packet}. An accepted packet is the
tuple $\mathcal{I}=(S,C,H,L,\rho,\lambda)$, where $S$ and $C$ are precisely the
consumed simplicial-set and category certificate rows.

The ledgers are also displayed tuple fields. The horn ledger $H$ records the
finite inner-horn rows, while the lifting ledger $L$ records the lifting
entries and their $\mathsf{ProbeBundle}$ support. The remaining tuple fields
$\rho$ and $\lambda$ provide the $\Pkg$ provenance and the $\Cont/\hsame$
transport rows. No additional coordinate is present, so this list is the full
inventory.
\end{proof}

\begin{theorem}[InfCatUp source and classifier obligations]
\label{thm:infcat-source-and-classifier-obligations}
The source and classifier obligations of an accepted $\InfCatUp$ packet are
exactly the fields listed in
\autoref{thm:infcat-obligation-inventory-fields}, together with componentwise
$\hsame/\Cont$ transport across the displayed packet coordinates. They include
no host quasicategory coordinate and no localization coordinate.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_source\_classifier\_obligations}
\begin{proof}
The source side is obtained by unfolding
\autoref{def:infcat-bhist-source-packet}: every admissible source read is one
of $S$, $C$, $H$, $L$, $\rho$, or $\lambda$, or a finite row projected from the
horn or lifting ledgers.

For the classifier side, apply
\autoref{thm:infcat-quasicategory-classifier-surface}. The classifier compares
the same packet coordinates through the consumed dependency classifiers,
componentwise $\hsame$, $\Cont$ transport, and shared $\Pkg$ provenance.

Since neither the packet definition nor the classifier surface supplies a host
quasicategory or localization slot, neither kind of coordinate can appear among
the source or classifier obligations.
\end{proof}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_source\_classifier\_obligation\_surface}

\begin{theorem}[InfCatUp stability, exactness, and ledger obligations]
\label{thm:infcat-stability-exactness-ledger-obligations}
For an accepted $\InfCatUp$ packet, the stability, exactness, ledger, and
downstream-consumer obligations are discharged by the inner-horn ledger
boundary, the quasicategory classifier surface, the NameCert obligation
surface, and the consumer boundary stated in this chapter.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_stability\_exactness\_ledger\_obligations}
\begin{proof}
Begin with the ledger part. The inner-horn ledger boundary theorem
\autoref{thm:infcat-inner-horn-ledger-boundary} restricts every horn read to
the displayed simplicial-set row, finite horn ledger, provenance row, and
transport ledger.

Next use the classifier surface of
\autoref{thm:infcat-quasicategory-classifier-surface}. It supplies the
componentwise $\hsame/\Cont$ transport needed for stability under displayed
replacement of the packet coordinates.

The exact obligation package is then read through
\autoref{thm:infcat-namecert-obligation-surface}. Finally,
\autoref{thm:infcat-consumer-boundary} identifies the downstream consumer
boundary with the same consumed certificate rows, finite ledgers, provenance,
and transport fields. These cited surfaces together exhaust the claimed
obligation families.
\end{proof}

\begin{theorem}[InfCatUp inner-horn ledger boundary]
\label{thm:infcat-inner-horn-ledger-boundary}
Every accepted $\InfCatUp$ source packet of
\autoref{def:infcat-bhist-source-packet} exposes its inner-horn data only
through the consumed $\NameCert_{\SimplicialSetUp}$ row $S$, the finite
inner-horn ledger $H$, the $\Pkg$ provenance row $\rho$, and the
$\Cont/\hsame$ transport ledger $\lambda$. Thus a consumer of the
inner-horn boundary cannot read a host quasicategory, a localization, or a
simplicial mapping object.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_inner\_horn\_ledger\_boundary}
\begin{proof}
Project an accepted packet
$\mathcal{I}=(S,C,H,L,\rho,\lambda)$. The horn boundary, missing inner face,
filler endpoint, and boundary comparison rows are exactly the entries of
$H$, and each of those entries is scoped by the simplicial-set carrier and
classifier rows supplied by $S$.

The provenance and transport reads are also displayed. The row $\rho$ records
which packet face supplied the horn entry, while $\lambda$ transports the
horn boundary, filler endpoint, and comparison rows through $\Cont$ and
$\hsame$.

No other tuple coordinate is available for an inner-horn read. In particular,
the category dependency $C$ and lifting ledger $L$ are not host
quasicategory data, and the tuple has no localization or simplicial
mapping-object slot. Repacking the projected rows gives exactly the stated
boundary.
\end{proof}

\begin{theorem}[InfCatUp quasicategory classifier surface]
\label{thm:infcat-quasicategory-classifier-surface}
For two $\InfCatUp$ source packets, the quasicategory classifier surface
compares only the displayed $\mathsf{BHist}$ rows $S$, $C$, $H$, $L$,
$\rho$, and $\lambda$ by the simplicial-set classifier, the category
classifier, componentwise $\hsame$, $\Cont$ transport, and shared $\Pkg$
provenance. It supplies no classifier for a host quasicategory, a
localization, or a simplicial mapping object.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_quasicategory\_classifier\_surface}
\leanvariant{BEDC.Derived.InfCatUp.InfCatQuasicategoryClassifierSurface\_transport}
\begin{proof}
Begin with the two consumed certificate rows. The simplicial-set dependency
classifies simplicial carrier, face, degeneracy, and simplex rows, while the
category dependency classifies the ordinary categorical source faces that
are explicitly present in the packet.

Next compare the horn and lifting ledgers. The entries of $H$ and $L$ are
finite $\mathsf{BHist}$ rows, so their comparisons are componentwise
$\hsame$ rows carried by the ledger $\lambda$. Continuation endpoints move
through the displayed $\Cont$ entries, and the package row $\rho$ keeps the
same provenance attached to the transported packet.

Repack these comparisons as the classifier surface. Since every compared
coordinate is one of $S$, $C$, $H$, $L$, $\rho$, or $\lambda$, there is no
remaining field from which a host quasicategory classifier, localization
classifier, or mapping-object classifier could be read.
\end{proof}

\begin{theorem}[InfCatUp NameCert obligation surface]
\label{thm:infcat-namecert-obligation-surface}
The $\NameCert_{\InfCatUp}$ obligation surface of an accepted packet
$\mathcal{I}=(S,C,H,L,\rho,\lambda)$ consists exactly of the
$\mathsf{BHist}$ source packet of
\autoref{def:infcat-bhist-source-packet}, the inner-horn ledger boundary of
\autoref{thm:infcat-inner-horn-ledger-boundary}, and the quasicategory
classifier surface of
\autoref{thm:infcat-quasicategory-classifier-surface}. Its rows are the
consumed $\NameCert_{\SimplicialSetUp}$ row, the consumed
$\NameCert_{\CategoryUp}$ row, the inner-horn ledger, the lifting witness
ledger, the $\Pkg$ provenance row, and the $\Cont/\hsame$ transport ledger,
with no host quasicategory, localization, or simplicial mapping object.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_namecert\_obligation\_surface}
\begin{proof}
Soundness is by projection from the source packet. The carrier row exposes
only $S$, $C$, $H$, $L$, $\rho$, and $\lambda$, the horn theorem reads the
inner-horn boundary from $S$, $H$, $\rho$, and $\lambda$, and the classifier
theorem compares those same displayed packet coordinates.

Completeness is the reverse reading. Any row used by carrier admission,
classifier transport, horn filling, lifting witness readback, provenance, or
continuation transport is one of the six packet coordinates or a projected
entry of $H$, $L$, $\rho$, or $\lambda$.

Therefore the naming-certificate obligation surface is exactly the displayed
finite packet and its projected horn and classifier rows. The proof never
opens a host quasicategory, localization, or simplicial mapping-object
coordinate, because the packet has no such coordinate.
\end{proof}

\begin{theorem}[InfCatUp consumer boundary]
\label{thm:infcat-consumer-boundary}
Every downstream consumer of the $\InfCatUp$ root reads through the displayed
$\mathsf{BHist}$ packet $(S,C,H,L,\rho,\lambda)$, the two consumed
$\NameCert$ rows $S$ and $C$, the finite inner-horn and lifting ledgers
$H$ and $L$, the $\Pkg$ provenance row $\rho$, and the $\Cont/\hsame$
transport ledger $\lambda$. Conversely those rows supply the complete
consumer boundary for the root, and no consumer obtains a host
quasicategory, localization, or simplicial mapping object.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_consumer\_boundary}
\begin{proof}
Project any accepted consumer read to the packet coordinates. A simplicial
read factors through $S$, an ordinary categorical source read factors through
$C$, an inner-horn read factors through $H$, and a lifting-witness read
factors through $L$.

The remaining consumer information is provenance and transport. The package
row $\rho$ records which dependency or ledger supplies the read, and the
ledger $\lambda$ records the $\Cont$ and $\hsame$ movements needed to keep the
read stable under displayed replacement.

For the converse, repack these projected rows into the source packet and use
\autoref{thm:infcat-namecert-obligation-surface}. It identifies the same rows
as the complete naming-certificate surface, so they already supply every
consumer-facing obligation. Since no projected coordinate names a host
quasicategory, localization, or simplicial mapping object, no downstream
consumer can read one from this root.
\end{proof}

\begin{theorem}[InfCatUp public certificate boundary]
\label{thm:infcat-public-certificate-boundary}
The public $\NameCert_{\InfCatUp}$ surface is exactly the consumed
$\NameCert_{\SimplicialSetUp}$ row, the consumed $\NameCert_{\CategoryUp}$ row,
the finite inner-horn ledger, the lifting ledger, the package provenance row,
and the $\Cont/\hsame$ transport ledger. No host quasicategory, localization,
or simplicial mapping object is part of the public certificate boundary.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_public\_certificate\_boundary}
\begin{proof}
First project the finite horn part by
\autoref{thm:infcat-inner-horn-ledger-boundary}. The inner-horn boundary is read
through the consumed simplicial-set row, the horn ledger, provenance, and
displayed transport.

Next use \autoref{thm:infcat-quasicategory-classifier-surface}. The classifier
surface compares only the displayed packet coordinates and their componentwise
$\hsame$ and $\Cont$ rows, so it adds no host quasicategory, localization, or
mapping-object coordinate.

Now apply \autoref{thm:infcat-namecert-obligation-surface}. It identifies the
NameCert obligations with the consumed simplicial-set and category rows,
inner-horn ledger, lifting ledger, package provenance, and transport ledger.

Finally read the downstream boundary through
\autoref{thm:infcat-consumer-boundary}. Its converse direction repacks exactly
those rows as the complete consumer surface, so the public certificate boundary
is precisely the displayed finite packet surface and nothing outside it.
\end{proof}

\begin{theorem}[InfCatUp inner-horn consumer determinacy]
\label{thm:infcat-inner-horn-consumer-determinacy}
For any accepted $\InfCatUp$ packet
$\mathcal{I}=(S,C,H,L,\rho,\lambda)$, every downstream consumer read of an
inner-horn or lifting obligation is determined entirely by the displayed
$\mathsf{BHist}$ rows $(S,C,H,L,\rho,\lambda)$, the consumed
$\NameCert_{\SimplicialSetUp}$ and $\NameCert_{\CategoryUp}$ rows, the finite
$\mathsf{ProbeBundle}$ horn and lifting ledger entries, $\Pkg$ provenance, and
$\Cont/\hsame$ transport. No host quasicategory, localization, or simplicial
mapping-object coordinate can change the read.
\end{theorem}
\begin{proof}
Project the consumer through \autoref{thm:infcat-consumer-boundary}. Any
inner-horn read is already a read of $S$, $H$, $\rho$, and $\lambda$, while any
lifting-obligation read is already a read of $S$, $C$, $L$, $\rho$, and
$\lambda$.

Restrict the inner-horn part by
\autoref{thm:infcat-inner-horn-ledger-boundary}. The horn boundary, missing
face, filler endpoint, and comparison rows are finite ledger entries carried by
$H$, with provenance supplied by $\rho$ and displayed transport supplied by
$\lambda$.

Transport equality of consumer reads through
\autoref{thm:infcat-quasicategory-classifier-surface}. Since the classifier
compares only the six packet coordinates and their consumed certificate rows,
equal displayed packets give equal downstream reads of the horn and lifting
surfaces.

Finally repack the exact surface by
\autoref{thm:infcat-namecert-obligation-surface}. The repacked surface contains
only the consumed certificate rows, the finite horn and lifting ledgers,
provenance, and $\Cont/\hsame$ transport. A host quasicategory, localization,
or simplicial mapping-object coordinate is therefore not available to affect
the read.
\end{proof}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_inner\_horn\_consumer\_determinacy}

\begin{theorem}[InfCatUp root-threshold obligation triad]
\label{thm:infcat-root-threshold-obligation-triad}
Every accepted $\InfCatUp$ source packet supplies exactly three downstream root
surfaces: the consumed $\NameCert_{\SimplicialSetUp}$ row, the consumed
$\NameCert_{\CategoryUp}$ row, and the finite inner-horn plus lifting-ledger
surface carried by $\mathsf{ProbeBundle}$, $\Cont$, $\hsame$, and $\Pkg$ rows.
Host quasicategory, localization, and simplicial mapping-object data are not
available to downstream category consumers at this root threshold.
\end{theorem}
\leanchecked{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_root\_threshold\_obligation\_triad}
\begin{proof}
Project the accepted packet as
$\mathcal{I}=(S,C,H,L,\rho,\lambda)$. The two consumed certificate rows are
the $S$ and $C$ coordinates, and the finite obligation surface is read through
the horn and lifting ledgers $H$ and $L$ with provenance $\rho$ and transport
$\lambda$.

Apply \autoref{thm:infcat-inner-horn-ledger-boundary} to identify the finite
inner-horn side of the surface. Apply
\autoref{thm:infcat-quasicategory-classifier-surface} to see that the
classifier compares only displayed packet coordinates and the componentwise
$\hsame/\Cont$ rows.

Now use \autoref{thm:infcat-namecert-obligation-surface} and
\autoref{thm:infcat-consumer-boundary}. Together they repackage the two
consumed NameCert rows and the horn-plus-lifting ledger as the full downstream
consumer boundary. Since no projected coordinate names a host quasicategory,
localization, or simplicial mapping object, those data remain unavailable at
the root threshold.
\end{proof}

\closureat{InfCatUp}{scopedStr}[BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_consumer\_boundary]
\closureat{InfCatUp}{publicStr}[BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_consumer\_boundary]
\closureat{InfCatUp}{bridgedStr}[BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_public\_certificate\_boundary]
\begin{closurestatus}{\InfCatUp}
  \constructivestory{An InfCat packet is generated from consumed $\SimplicialSetUp$ and $\CategoryUp$ certificate rows, finite inner-horn and lifting ledgers, one provenance package, and rowwise $\Cont/\hsame$ transport. The checked consumer boundary exposes only those displayed packet rows to downstream category consumers.}
  \theoryclosure{\bridgedClosure}
  \scopeclosed{The public certificate boundary of \autoref{thm:infcat-public-certificate-boundary} binds the consumed $\SimplicialSetUp$ and $\CategoryUp$ rows, finite inner-horn and lifting ledgers, $\mathsf{ProbeBundle}$, $\Cont$, $\hsame$, and $\Pkg$ rows displayed by the scoped source-packet surface of \autoref{thm:infcat-inner-horn-ledger-boundary}, \autoref{thm:infcat-quasicategory-classifier-surface}, \autoref{thm:infcat-namecert-obligation-surface}, and \autoref{thm:infcat-consumer-boundary}.}
  \formalstatus{\axiomCleanV}
  \leantarget{BEDC.Derived.InfCatUp.InfCatBHistSourcePacket\_public\_certificate\_boundary}
  \bridgestatus{paperBridge}
  \notclaimed{Host quasicategories, localization, and simplicial mapping objects are not closed.}
  \upgradepath{Mature closure requires a finite consumer-completeness surface for the bridged InfCat packet, without claiming host quasicategories or localization.}
\end{closurestatus}
