\chapter{A Concrete Naming Certificate for $\CanonicalTailChoiceUp$}
\label{ch:concrete-instances-canonical-tail-choice-namecert}
\origin{ai}

The $\CanonicalTailChoiceUp$ packet realizes the finite tail-choice route needed by the Real-completeness limit theorem of \autoref{ch:visions-real-completeness}. It sits after the no-choice boundary of \autoref{ch:concrete-instances-cauchy-choice-boundary-namecert}, the shared tail schedule of \autoref{ch:concrete-instances-tail-cofinality-schedule-namecert}, the bounded prefix budget of \autoref{ch:concrete-instances-finite-prefix-limit-budget-namecert}, and the exact completion boundary of \autoref{ch:concrete-instances-real-completion-exact-boundary-namecert}. Its role is to expose the canonical finite index and tail-window witness used before the diagonal seal is read, without importing a host-selected subsequence, quotient stream equality, countable choice row, or ambient completeness principle.

\falsifiablePrediction{A Real-completion consumer that omits the canonical finite tail-choice row cannot claim the diagonal seal handoff.}

\independenceWitness{cauchychoiceboundary, tailcofinalityschedule, finiteprefixlimitbudget, realcompletionexactboundary, limitselector: none is bijective to $\CanonicalTailChoiceUp$ because this packet simultaneously carries the modulus row, tolerance-budget row, canonical finite index row, tail-window witness row, Real seal route, no-choice refusal row, componentwise transport, continuation replay, provenance, and local naming surface; the named siblings isolate boundary refusal, cofinal scheduling, prefix-budget exhaustion, exact boundary faces, or selector admission without this joint carrier.}

\begin{definition}[Canonical tail-choice carrier]
\label{def:canonical-tail-choice-carrier}
A $\CanonicalTailChoiceUp$ carrier is a finite $\BHist$ packet
$$
C=(M,E,I,T,S,R,H,C_0,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $M$ is the modulus row read from the accepted regular-Cauchy route;
\item $E$ is the tolerance-budget row fixing the finite precision scale served by the packet;
\item $I$ is the canonical finite index row computed from $M$ and $E$, not from an external choice schedule;
\item $T$ is the tail-window witness row certifying that every downstream observation is read inside the finite tail determined by $I$;
\item $S$ is the $\RealUp$ seal route reached only after $M,E,I,T$ have been displayed;
\item $R$ is the no-choice refusal row excluding host-selected limits, quotient stream equality, countable choice, hidden tail oracles, and ambient completeness;
\item $H$ records componentwise $\hsame$ transport for the displayed analytic rows and the structural rows;
\item $C_0$ records the displayed $\Cont$ replay from modulus and budget admission to canonical index, tail-window witness, Real seal, refusal, and local naming;
\item $P$ is the $\Pkg$ provenance over the sibling certificates, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\CanonicalTailChoiceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these ten rows. It has no coordinate for a host-selected subsequence, quotient stream equality, countable choice, metric completeness, ambient completeness, or a detached Real-completion seal.
\end{definition}
\leandef{BEDC.Derived.CanonicalTailChoiceUp.CanonicalTailChoiceUp}

\begin{theorem}[Canonical tail-choice NameCert obligations]
\label{thm:canonical-tail-choice-namecert-obligations}
For every accepted $\CanonicalTailChoiceUp$ carrier
$$
C=(M,E,I,T,S,R,H,C_0,P,N),
$$
the local $\NameCert_{\CanonicalTailChoiceUp}$ surface consists exactly of carrier exposure for $C$, modulus exposure through $M$, tolerance-budget exposure through $E$, canonical finite-index exposure through $I$, tail-window witness exposure through $T$, $\RealUp$ seal-route exposure through $S$, no-choice refusal through $R$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C_0$, package provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:canonical-tail-choice-carrier}. Its displayed rows list the modulus, tolerance budget, canonical finite index, tail-window witness, seal route, refusal ledger, and structural support.

Read the rows in order. The modulus row $M$ and tolerance-budget row $E$ determine the finite index row $I$ before the tail-window witness $T$ can be consumed. The Real seal route $S$ is therefore downstream from a displayed finite choice, not from a hidden selector.

Finally inspect the structural rows. The rows $H,C_0,P,N$ transport, replay, record provenance for, and name the same finite packet. Since no further coordinate occurs in the carrier, the listed rows exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Canonical tail-choice schedule factorization]
\label{thm:canonical-tail-choice-schedule-factorization}
Every accepted Real-completion consumer of a $\CanonicalTailChoiceUp$ packet factors through the finite route
$$
M,E,I,T,S,R,H,C_0,P,N.
$$
When the consumer also reads the sibling surfaces of \autoref{ch:concrete-instances-tail-cofinality-schedule-namecert} and \autoref{ch:concrete-instances-finite-prefix-limit-budget-namecert}, their schedule and prefix-budget rows attach before the tail-window witness $T$ and before the Real seal route $S$.
\end{theorem}
\begin{proof}
Start with the obligation surface of \autoref{thm:canonical-tail-choice-namecert-obligations}. The canonical finite index $I$ is exposed only after $M$ and $E$, so any downstream schedule must already have the modulus and tolerance budget in scope.

Attach the cofinal schedule. The $\TailCofinalityScheduleUp$ packet supplies its finite window and dyadic threshold rows as an accepted sibling route, and those rows can be consumed only through the same displayed finite schedule surface.

Attach the prefix budget next. The $\FinitePrefixLimitBudgetUp$ packet records which prefix windows have been spent before a seal-facing read is admitted. Thus the local tail-window witness $T$ is reached only after the sibling schedule and prefix-budget rows have been displayed.

The remaining rows $S,R,H,C_0,P,N$ keep the seal route and refusal ledger inside that same finite packet, so every accepted consumer factors through the stated route.
\end{proof}

\begin{theorem}[Canonical tail-choice no-choice non-escape]
\label{thm:canonical-tail-choice-no-choice-nonescape}
No host-selected limit, quotient stream equality, countable choice row, hidden tail oracle, metric completeness row, ambient completeness row, or detached Real-completion seal can be read from an accepted $\CanonicalTailChoiceUp$ packet. The packet exports only the rows $M,E,I,T,S,R,H,C_0,P,N$ of \autoref{def:canonical-tail-choice-carrier}.
\end{theorem}
\begin{proof}
Inspect the accepted carrier. The refusal row $R$ is a displayed coordinate, while none of the excluded objects is a coordinate of the tuple.

Apply \autoref{thm:canonical-tail-choice-schedule-factorization}. Every accepted consumer reaches the Real seal route only through $M,E,I,T,S,R,H,C_0,P,N$, with sibling schedule and prefix-budget rows consumed before the tail-window witness.

The finite index row $I$ is not a host-selected limit or a countable-choice schedule; it is the canonical row displayed after $M$ and $E$. The witness row $T$ and seal row $S$ are likewise route coordinates, not quotient equalities or completeness principles. Hence any read of an excluded object leaves the accepted packet.
\end{proof}

\begin{theorem}[Canonical tail-choice Real-completion handoff]
\label{thm:canonical-tail-choice-real-completion-handoff}
The Real-completion diagonal seal handoff may consume an accepted $\CanonicalTailChoiceUp$ packet only through the displayed route
$$
M,E,I,T,S,R,H,C_0,P,N.
$$
Under \autoref{ch:concrete-instances-cauchy-choice-boundary-namecert} and \autoref{ch:concrete-instances-real-completion-exact-boundary-namecert}, this route supplies the finite tail-choice row between no-choice refusal and the terminal exact-boundary seal, and supplies no host-side equality or ambient completeness data.
\end{theorem}
\begin{proof}
Begin with the no-choice boundary. The sibling $\CauchyChoiceBoundaryUp$ surface already requires a displayed finite index, tail witness, seal route, and refusal row before a diagonal consumer may claim the no-choice seal path.

Next apply the local obligations and schedule factorization. The $\CanonicalTailChoiceUp$ packet identifies the canonical finite index $I$ and tail-window witness $T$ as first-class rows between the modulus-budget pair $M,E$ and the Real seal route $S$.

Finally read the exact boundary. The $\RealCompletionExactBoundaryUp$ packet admits terminal completion reads only through its displayed StreamName, RegSeqRat, DyadicRatCore, and RealUp faces. Since the present packet exports only $M,E,I,T,S,R,H,C_0,P,N$ and the sibling boundary exports no hidden selector, the diagonal seal handoff remains a finite no-choice route.
\end{proof}

The Lean follow-up namespace is \texttt{BEDC.Derived.CanonicalTailChoiceUp}. Its \texttt{TasteGate.lean} surface must provide \texttt{Nontrivial} and \texttt{FieldFaithful} instances for the carrier of \autoref{def:canonical-tail-choice-carrier}.

\closureat{CanonicalTailChoiceUp}{seedStr}

\begin{closurestatus}{\CanonicalTailChoiceUp}
  \constructivestory{A $\CanonicalTailChoiceUp$ packet is generated from a regular-Cauchy modulus row, a finite tolerance-budget row, a canonical finite-index row, a tail-window witness row, a Real seal route, a no-choice refusal row, componentwise transports, continuation replay, provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:canonical-tail-choice-carrier}, \autoref{thm:canonical-tail-choice-namecert-obligations}, \autoref{thm:canonical-tail-choice-schedule-factorization}, \autoref{thm:canonical-tail-choice-no-choice-nonescape}, and \autoref{thm:canonical-tail-choice-real-completion-handoff} declare the finite tail-choice packet and its Real-completion handoff surface.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{ai}
  \notclaimed{This chapter does not close RealUp completeness, quotient-stream equality, host real equality, countable choice, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, canonical-index exactness, schedule factorization, no-choice refusal, Real-completion handoff, and TasteGate carrier support for the same packet.}
\end{closurestatus}
