\chapter{A Concrete Naming Certificate for $\StreamDiagonalSelectorUp$}
\label{ch:concrete-instances-stream-diagonal-selector-namecert}
\origin{human}

The $\StreamDiagonalSelectorUp$ interface packages the finite diagonal selector row used between $\StreamNameUp$, $\RegSeqRatUp$, and $\RealDiagonalCompletionUp$. Following Bishop-style constructive diagonalization, a consumer precision request is answered by an explicit finite stream window, a regular-rational readback, a dyadic observation ledger, and a diagonal-completion packet. The certificate does not classify quotient streams, select a completed real by choice, or compare host real equality.

The selector is the finite routing surface between \autoref{ch:concrete-instances-regularcauchyname-namecert} and \autoref{ch:concrete-instances-real-diagonal-completion-namecert}. It consumes the RegularCauchyName stream-window and dyadic-readback rows, then hands the same selected window to the RealDiagonalCompletion packet before any $\RealUp$ seal can be read.

\begin{definition}[StreamDiagonalSelector carrier]
\label{def:stream-diagonal-selector-carrier}
A $\StreamDiagonalSelectorUp$ carrier is a finite $\BHist$ packet
$$
D=(S,\mu,W,R,D_H,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $S$ is the $\StreamNameUp$ schedule naming the finite stream windows that may be inspected by the diagonal consumer;
\item $\mu$ is the displayed selector row assigning each unary precision request to the diagonal window index read from $S$;
\item $W$ is the selected finite $\StreamNameUp$ window, including the member index and observation index used by the diagonal read;
\item $R$ is the $\RegSeqRatUp$ readback row naming the rational observation extracted from the selected window;
\item $D_H$ is the $\DyadicRatCoreUp$ observation ledger recording the endpoint, radius, comparison, and precision rows attached to the readback;
\item $H$ records the $\RealDiagonalCompletionUp$ packet that consumes the same selected window, readback, and dyadic ledger;
\item $C$ records the displayed $\Cont$ routes from the selector request to $S$, $\mu$, $W$, $R$, $D_H$, and $H$;
\item $P$ is the $\Pkg$ provenance over $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\RealDiagonalCompletionUp$, $\RealUp$, $\BHist$, $\hsame$, and $\Cont$;
\item $N$ is the local $\NameCert_{\StreamDiagonalSelectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through the listed finite rows, their componentwise $\hsame$ transports, the displayed $\Cont$ routes, package provenance, and local naming row. It has no coordinate for a quotient stream, choice-selected limit, external real value, or host equality test.
\end{definition}
\leanchecked{BEDC.Derived.StreamDiagonalSelectorUp.TasteGate.StreamDiagonalSelectorTasteGate\_single\_carrier\_alignment}

\begin{theorem}[StreamDiagonalSelector NameCert obligations]
\label{thm:stream-diagonal-selector-namecert-obligations}
The local $\NameCert_{\StreamDiagonalSelectorUp}$ obligation surface consists of five finite rows:
\begin{enumerate}
\item carrier habitation: the finite packet of \autoref{def:stream-diagonal-selector-carrier} stores the stream schedule, selector row, selected window, rational readback, dyadic observation ledger, diagonal-completion packet, transport routes, package provenance, and local naming row;
\item selector determinacy: for each displayed precision request, the selected window is the one read from $\mu$ and $S$, so two accepted packets with the same transported selector rows expose the same diagonal window coordinate;
\item finite-window transport: the $\StreamNameUp$ window, $\RegSeqRatUp$ readback, and $\DyadicRatCoreUp$ ledger transport together along the componentwise $\hsame$ and $\Cont$ rows recorded in $C$;
\item diagonal handoff exactness: the $\RealDiagonalCompletionUp$ packet $H$ consumes exactly the selected window $W$, readback $R$, dyadic ledger $D_H$, package provenance $P$, and local naming row $N$;
\item non-escape: every consumer-visible read is exhausted by the displayed selector packet and exports no quotient stream, no choice-selected limit, no host real equality, and no external completed-real carrier.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.StreamDiagonalSelectorUp.StreamDiagonalSelectorTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier habitation is obtained by projecting the finite history packet. The schedule $S$, selector row $\mu$, selected window $W$, readback $R$, dyadic ledger $D_H$, diagonal packet $H$, continuation routes, package provenance, and local naming row are all named coordinates.

Selector determinacy follows because $\mu$ is part of the displayed packet. A precision request cannot select a different window without leaving the recorded route through $S$ and $\mu$, and the classifier exposes only the transported versions of those two rows.

For finite-window transport, move $S$, $\mu$, and $W$ by the componentwise $\hsame$ rows and replay the $\Cont$ routes in $C$. The readback $R$ and ledger $D_H$ are attached to that same selected window, so they move with it as a single finite observation.

The diagonal handoff is the projection to $H$. Since $H$ is stored beside $W$, $R$, $D_H$, $P$, and $N$, the $\RealDiagonalCompletionUp$ consumer receives precisely those rows and no hidden selector.

Finally inspect the carrier shape. There is no field for quotient stream equality, a choice-selected limit, host real equality, or an external completed real, so the local naming certificate cannot export any such datum.
\end{proof}

\begin{theorem}[StreamDiagonalSelector RealUp handoff]
\label{thm:stream-diagonal-selector-real-handoff}
For every accepted $\StreamDiagonalSelectorUp$ carrier $D=(S,\mu,W,R,D_H,H,C,P,N)$, every downstream $\RealUp$ read factors through the selected finite $\StreamNameUp$ window $W$, the $\RegSeqRatUp$ readback $R$, the $\DyadicRatCoreUp$ observation ledger $D_H$, and the $\RealDiagonalCompletionUp$ packet $H$. The handoff supplies a finite real-facing observation route and does not export a quotient stream, a choice-selected limit, a host real value, or host real equality.
\end{theorem}
\leanchecked{BEDC.Derived.StreamDiagonalSelectorUp.StreamDiagonalSelectorPacket\_real\_handoff}
\begin{proof}
Start from a downstream $\RealUp$ read and project the carrier. The only route from a precision request to a stream observation is the displayed path through $S$, $\mu$, and the selected finite window $W$.

The selected window is then read through the regular rational row $R$. The dyadic ledger $D_H$ records the endpoint, radius, precision, and comparison data consumed by that readback, so the observation is a finite BEDC row rather than an external stream value.

The $\RealDiagonalCompletionUp$ coordinate $H$ repacks the same $W$, $R$, and $D_H$ rows for the completion-facing boundary. Replaying the routes in $C$ and the provenance in $P$ keeps the downstream $\RealUp$ consumer inside the same local $\NameCert$ packet.

Since the carrier has no further coordinate beyond those rows, no quotient stream, choice-selected limit, host real value, or host real equality can be read from the handoff.
\end{proof}

\begin{theorem}[StreamDiagonalSelector selector determinacy]
\label{thm:stream-diagonal-selector-selector-determinacy}
If two accepted $\StreamDiagonalSelectorUp$ reads pass through the same displayed selector row $\mu$ and the same $\StreamNameUp$ schedule $S$, then they expose the same classifier-facing selected window coordinate. The determinacy is a statement about the visible selector packet and does not compare quotient streams, selected limits, host real values, or host equality.
\end{theorem}
\leanchecked{BEDC.Derived.StreamDiagonalSelectorUp.StreamDiagonalSelectorPacket\_selector\_determinacy}
\begin{proof}
Unpack the carrier of \autoref{def:stream-diagonal-selector-carrier}. A downstream precision request reaches a selected window only by reading the schedule $S$ and the selector row $\mu$.

The NameCert obligation surface in \autoref{thm:stream-diagonal-selector-namecert-obligations} records selector determinacy as one of the finite rows. Thus two reads through the same transported $S$ and $\mu$ expose the same selected window coordinate to the classifier.

Finally apply \autoref{thm:stream-diagonal-selector-real-handoff}. The handoff has no alternate coordinate for a quotient stream, selected completed value, external real carrier, or host equality test, so no second selector source can alter that coordinate.
\end{proof}

\begin{theorem}[StreamDiagonalSelector finite-window transport]
\label{thm:stream-diagonal-selector-window-transport}
The selected $\StreamNameUp$ window $W$, the $\RegSeqRatUp$ readback $R$, the $\DyadicRatCoreUp$ ledger $D_H$, and the $\RealDiagonalCompletionUp$ packet $H$ transport together through the recorded $\hsame$ and $\Cont$ rows of an accepted $\StreamDiagonalSelectorUp$ carrier.
\end{theorem}
\begin{proof}
Unpack the accepted packet in \autoref{def:stream-diagonal-selector-carrier}. The rows $W$, $R$, $D_H$, and $H$ are stored as the selected finite observation route, and the row $C$ stores the displayed continuation routes that connect them.

Use \autoref{thm:stream-diagonal-selector-namecert-obligations}. Its finite-window transport row states that the selected stream window, regular-rational readback, and dyadic ledger move together along the componentwise $\hsame$ and $\Cont$ rows.

The RealUp handoff of \autoref{thm:stream-diagonal-selector-real-handoff} consumes the same $W$, $R$, $D_H$, and $H$ rows. Therefore transport cannot detach the readback, ledger, or diagonal packet from the selected window.
\end{proof}

\begin{theorem}[StreamDiagonalSelector handoff exactness]
\label{thm:stream-diagonal-selector-handoff-exactness}
Every $\RealUp$ handoff from an accepted $\StreamDiagonalSelectorUp$ carrier consumes exactly the selected finite window $W$, readback row $R$, dyadic ledger $D_H$, diagonal-completion packet $H$, package row $P$, and local $\NameCert$ row $N$. It consumes no quotient stream, selected limit, host equality, or external completed-real carrier.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:stream-diagonal-selector-carrier}. The real-facing rows after selector evaluation are precisely $W$, $R$, $D_H$, $H$, $P$, and $N$, with the recorded routes in $C$ mediating access to them.

Apply \autoref{thm:stream-diagonal-selector-namecert-obligations}. Its handoff exactness and non-escape rows state that the diagonal packet consumes the selected finite window, readback, dyadic ledger, provenance, and local naming row without adding an external selector.

Finally use \autoref{thm:stream-diagonal-selector-real-handoff}. It identifies the downstream $\RealUp$ route with those same rows, so no quotient stream, selected completed value, host equality, or outside real carrier can be read by the handoff.
\end{proof}

\begin{theorem}[StreamDiagonalSelector tail-budget readback]
\label{thm:stream-diagonal-selector-tail-budget-readback}
Let $D=(S,\mu,W,R,D_H,H,C,P,N)$ be an accepted $\StreamDiagonalSelectorUp$ packet. If its selected finite window $W$ is consumed by an accepted $\RegularCauchyTailBudgetUp$ row, then the $\RealDiagonalCompletionUp$ handoff $H$ factors through the displayed $\StreamNameUp$ schedule $S$, selector row $\mu$, selected finite window $W$, $\DyadicRatCoreUp$ observation ledger $D_H$, $\RegSeqRatUp$ readback row $R$, the shared tail-threshold and observation-budget rows of the $\RegularCauchyTailBudgetUp$ packet, and the local $\NameCert$ route $N$.

Thus every such handoff remains a finite route through the selector packet and the tail-budget readback surface. It exports no quotient stream, selected host limit, ambient completeness principle, or host real equality.
\end{theorem}
\begin{proof}
Project the selector carrier. The only rows available to the diagonal consumer are the schedule $S$, selector row $\mu$, selected window $W$, readback row $R$, dyadic ledger $D_H$, diagonal packet $H$, routes $C$, provenance $P$, and local name $N$.

Use selector determinacy, finite-window transport, and handoff exactness. These results keep the selected window attached to the same schedule and selector row, move $W,R,D_H$ together through the displayed $\hsame$ and $\Cont$ data, and identify $H$ as the packet consuming exactly those rows.

Now apply the $\RegularCauchyTailBudgetUp$ observation gate and readback factorization to the budget row that consumes $W$. They route the window service through the shared tail threshold, observation budget, dyadic ledger, and $\RegSeqRatUp$ readback before any real-facing seal or completion-facing consumer is exposed.

Combining the two routes gives a single finite handoff from $S,\mu,W,D_H,R$ through the tail-budget rows to $H$ and $N$. Since neither carrier stores quotient streams, selected host limits, ambient completeness, or host real equality, no such datum can be read from the composed handoff.
\end{proof}

\closureat{StreamDiagonalSelectorUp}{seedStr}

\begin{closurestatus}{\StreamDiagonalSelectorUp}
  \constructivestory{A $\StreamDiagonalSelectorUp$ packet is generated from a $\StreamNameUp$ schedule, a displayed selector row, one selected finite stream window, a $\RegSeqRatUp$ readback, a $\DyadicRatCoreUp$ observation ledger, a $\RealDiagonalCompletionUp$ diagonal packet, displayed $\hsame$ and $\Cont$ routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:stream-diagonal-selector-carrier}, \autoref{thm:stream-diagonal-selector-namecert-obligations}, and \autoref{thm:stream-diagonal-selector-real-handoff} describe the seed finite diagonal selector certificate consumed by real-completion routes.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close RealUp completeness, uniqueness of completed limits, quotient equality of streams, a public standard bridge, or checked Lean implementation.}
  \upgradepath{Obligation closure requires checked carrier habitation, selector determinacy, finite-window transport, diagonal handoff exactness, and non-escape for $\StreamDiagonalSelectorUp$.}
\end{closurestatus}
