\chapter{A Concrete Naming Certificate for $\FieldExtUp$}
\label{ch:concrete-instances-fieldext-namecert}

The field-extension interface $\FieldExtUp$ packages an embedding of one field carrier into another, recording the larger field as a vector space over the smaller. It depends on $\NameCert_{\FieldUp}$ (\autoref{ch:concrete-instances-field-namecert}) and $\NameCert_{\VecSpaceUp}$ (\autoref{ch:concrete-instances-vecspace-namecert}), and is the substrate for Galois, separable, and algebraic-closure certificates.

\section{Carrier definition}
\label{sec:fieldext-carrier}

\begin{definition}[Concrete singleton empty-history field extension instance]
\label{def:fieldext-singleton-empty-history-instance}
Let the base field carrier and extension field carrier both be
$\mathsf{FieldSingletonCarrier}$ over $\mathsf{BHist}$, with field classifier
$\mathsf{FieldSingletonClassifier}$. Equivalently, this is the singleton
empty-history carrier $A_{\emp}$ with shared classifier
$$
\rho_{\emp}(h,k):=
A_{\emp}(h)\land A_{\emp}(k)\land\hsame(h,k).
$$
Both field endpoints use the singleton $\FieldUp$ operations of
Definition~\ref{def:singleton-empty-history-field-schema-instance} for both
the base and extension fields:
$\mathsf{FieldSingletonAdd}$, $\mathsf{FieldSingletonMul}$,
$\mathsf{FieldSingletonZero}$, $\mathsf{FieldSingletonOne}$,
$\mathsf{FieldSingletonNeg}$, and the proof-indexed inverse
$\mathsf{FieldSingletonInv}$. Define the embedding by
$\iota_{\emp}(h):=h$ on $\mathsf{BHist}$.

Read the extension as the singleton $\VecSpaceUp$ carrier
$\mathsf{VecSpaceSingletonCarrier}$ over the singleton scalar field. Its
vector classifier is $\mathsf{VecSpaceSingletonClassifier}$ and its scalar
action is $\mathsf{VecSpaceSingletonSmul}$. The ledger is inherited from the
singleton $\FieldUp$ certificate on the two field sides and from the singleton
$\VecSpaceUp$ certificate on the vector-space-over-base side.

The certificate fit has ten fields:
\begin{enumerate}
  \item Traditional target: the terminal field extension.
  \item BEDC source: $\mathsf{BHist}$.
  \item Carrier choice: $A_{\emp}$ for the base field, extension field, and
  vector carrier.
  \item Classifier choice: $\rho_{\emp}$ on all displayed endpoints.
  \item Stability obligations: the singleton field laws together with the
  singleton vector-space laws.
  \item Ledger: the identity embedding and vector-space provenance over the
  same empty-history endpoint.
  \item Core theorem list:
  Theorems~\ref{thm:fieldext-singleton-embedding-obligations},
  \ref{thm:fieldext-singleton-embedding-exactness},
  \ref{thm:fieldext-singleton-vector-space-over-base},
  \ref{thm:fieldext-singleton-embedded-scalar-action-collapse},
  \ref{thm:fieldext-singleton-carrier-coincidence},
  \ref{thm:fieldext-singleton-identity-tower-composition},
  \ref{thm:fieldext-singleton-exact-endpoint-ledger},
  \ref{thm:fieldext-singleton-exact-endpoint-classification},
  \ref{thm:fieldext-singleton-ledger-provenance}, and
  \ref{thm:fieldext-singleton-certificate-obligation-package}.
  \item Exactness predicate: singleton endpoint collapse.
  \item Standard bridge: the terminal field extension.
  \item Status: $\mathsf{ProofTarget}$.
\end{enumerate}
\end{definition}

\begin{definition}[Singleton FieldExt obligation scope]
\label{def:fieldext-singleton-obligation-scope}
The terminal $\FieldExtUp$ instance over $A_{\emp}$ is the following ten-field
paper template. The traditional target is the one-point field extension. The BEDC
source is $\mathsf{BHist}$. The base field carrier, extension field carrier, and
extension vector carrier are all $A_{\emp}$. The classifier is the shared
singleton relation $\rho_{\emp}$ from
Definition~\ref{def:fieldext-singleton-empty-history-instance}. The embedding is the
identity map $\iota_{\emp}(h):=h$. The extension-field vector-space-over-base
action is the singleton vector-space action over the singleton $\FieldUp$ source.

The stability obligations are the singleton field rows of
Theorem~\ref{thm:singleton-empty-history-field-schema-laws} for the base and
extension fields, together with the singleton vector-space rows of
Theorem~\ref{thm:singleton-empty-history-vecspace-laws}. The ledger consists of
identity-embedding provenance and singleton scalar-action provenance over the
same empty-history endpoint. The downstream consumers are the Galois,
number-field, and algebraic-closure certificate families, each of which reads the
same carrier, classifier, exactness, scalar-action, and ledger fields.
\end{definition}

\begin{definition}[RatUp reflexive field-extension carrier]
\label{def:fieldext-reflexive-extension-carrier}
Let the base field carrier and the ambient field carrier both be the concrete
$\FieldUp(\RatUp)$ carrier of
\autoref{def:ratup-fieldup-concrete-source-tuple}:
$$
C_{\mathsf{base}}=C_{\mathsf{amb}}=\mathsf{RatHistoryCarrier},
\qquad
R_{\mathsf{base}}=R_{\mathsf{amb}}=\mathsf{RatHistoryClassifier}.
$$
The classifier for the extension package is the RatUp classifier on the same
$\mathsf{BHist}$ endpoints. The embedding is the identity map
$\iota_{\mathsf{Rat}}(h):=h$ on $\mathsf{BHist}$.

The ambient field is also used as its own vector carrier over the base field.
Scalar multiplication is the $\FieldUp(\RatUp)$ multiplication row of
\autoref{thm:ratup-fieldup-assembled-certificate-boundary}, and vector
addition, zero, and negation are the additive rows retained by the same
FieldUp certificate through the commutative-ring and ring reducts. Thus the
displayed object is the reflexive field extension
$$
\RatUp \hookrightarrow \RatUp
$$
with no change of BEDC carrier, classifier, ledger source, or operation table.
\end{definition}

\begin{theorem}[Singleton field-extension embedding obligations]
\label{thm:fieldext-singleton-embedding-obligations}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, let
$h,k:\mathsf{BHist}$ be carried by $\mathsf{FieldSingletonCarrier}$. Then
$\iota_{\emp}(h)$ is carried by the extension field,
$$
\mathsf{FieldSingletonClassifier}(h,k)\quad\text{if and only if}\quad
\mathsf{FieldSingletonClassifier}(\iota_{\emp}(h),\iota_{\emp}(k)),
$$
and the embedding preserves the concrete singleton zero, one, addition,
negation, multiplication, and proof-indexed inverse up to $\rho_{\emp}$.
Thus the base endpoint and its embedded extension endpoint have the same
singleton classification for each displayed field operation.
\end{theorem}
\leanchecked{BEDC.Derived.FieldExtUp.FieldExtSingletonEmbedding\_laws}
\begin{proof}
Unfold $\iota_{\emp}$. The carrier statement is immediate from the assumption
$A_{\emp}(h)$, because the base and extension field carriers are the same
singleton carrier $A_{\emp}$.

The classifier comparison has the same two directions. After unfolding the
identity embedding, both sides are the identical classifier assertion
$\rho_{\emp}(h,k)$.

For zero, one, addition, negation, and multiplication, apply
Theorem~\ref{thm:singleton-empty-history-field-schema-laws} to obtain the
field-law rows over $\mathsf{FieldSingletonCarrier}$ and
$\mathsf{FieldSingletonClassifier}$. Then use
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse} to read
each concrete operation endpoint as the singleton empty-history endpoint.

For the inverse rows, fix a proof-indexed witness in the singleton nonzero
domain. The same operation-table collapse theorem gives the inverse endpoint
row for $\mathsf{FieldSingletonInv}(h,p)$, and the law package uses that same
proof-indexed domain. Hence base inverse and embedded extension inverse are
classified by $\rho_{\emp}$ at the same singleton endpoint.
\end{proof}

\begin{theorem}[Singleton FieldExt embedding exactness]
\label{thm:fieldext-singleton-embedding-exactness}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, let
$h,k:\mathsf{BHist}$ be carried by $A_{\emp}$. Then
$$
\rho_{\emp}(h,k)\quad\text{if and only if}\quad
\rho_{\emp}(\iota_{\emp}(h),\iota_{\emp}(k)).
$$
Moreover, for every displayed singleton field operation in the base package, its
embedded extension endpoint is classified with the corresponding source endpoint
by $\rho_{\emp}$.
\end{theorem}
\begin{proof}
Unfold $\iota_{\emp}$. The displayed equivalence is the classifier comparison
recorded in Theorem~\ref{thm:fieldext-singleton-embedding-obligations}; after the
identity embedding is unfolded, both sides are the same singleton classifier
assertion.

For the operation endpoints, apply
Theorem~\ref{thm:fieldext-singleton-embedding-obligations} to the carried inputs. It
gives preservation of zero, one, addition, negation, multiplication, and the
proof-indexed inverse up to $\rho_{\emp}$.

The concrete endpoint identification comes from the singleton operation-table
collapse in Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}.
Thus each embedded operation row lands in the same $\rho_{\emp}$ class as its
source row.
\end{proof}

\section{The certificate}
\label{sec:fieldext-certificate}

\input{parts/concrete_instances/fieldext/ratup_reflexive_certificate}

\begin{theorem}[RatUp reflexive FieldExt operation-table coverage]
\label{thm:fieldext-ratup-reflexive-operation-table-coverage}
For the concrete package of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, every base-field
row, ambient-field row, vector addition row, vector zero row, vector negation
row, and scalar-action row is read from
\autoref{thm:ratup-fieldup-assembled-certificate-boundary} over
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$. The
base-field and ambient-field operation tables are the same concrete
$\FieldUp(\RatUp)$ operation table, while the vector-space additive rows and
scalar-action row are the corresponding additive and multiplication rows of
that table.
\end{theorem}
\begin{proof}
Unfold Definition~\ref{def:fieldext-reflexive-extension-carrier}. The
embedding $\iota_{\mathsf{Rat}}$ is the identity on $\mathsf{BHist}$, so the
base and ambient endpoints are not transported to a distinct carrier or
classifier.

Read \autoref{thm:ratup-fieldup-assembled-certificate-boundary} once for the
base field and once for the ambient field. Both readings use
$\mathsf{RatHistoryCarrier}$, $\mathsf{RatHistoryClassifier}$, and the concrete
RatUp operation table.

For the vector-space rows, apply
\autoref{prop:vecspace-module-fragment-projection} to retain the scalar action
and module-shaped compatibility from the FieldUp multiplication and
distributivity rows. Then apply
\autoref{cor:vecspace-additive-carrier-projection} to retain the vector
addition, zero, negation, carrier, and classifier. Thus the FieldExt operation
table introduces no row outside the displayed RatUp FieldUp table.
\end{proof}

\begin{theorem}[RatUp reflexive scalar-action readback]
\label{thm:fieldext-ratup-reflexive-scalar-action-readback}
For the concrete package of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, the $\FieldExtUp$
scalar action is exactly the multiplication row of the concrete
$\FieldUp(\RatUp)$ certificate. For every scalar endpoint
$r:\mathsf{BHist}$ and vector endpoint $m:\mathsf{BHist}$ carried by
$\mathsf{RatHistoryCarrier}$, the scalar-action endpoint
$r\odot_{\mathsf{Rat}} m$ is the FieldUp product endpoint
$r\cdot_{\mathsf{Rat}} m$, and classifier stability is the multiplication
congruence row already included in
\autoref{thm:ratup-fieldup-assembled-certificate-boundary}.
\end{theorem}
\begin{proof}
Unfold the scalar action in
Definition~\ref{def:fieldext-reflexive-extension-carrier}. It is defined to be
the $\FieldUp(\RatUp)$ multiplication row, with no change of carrier,
classifier, or endpoint domain.

The assembled FieldUp certificate supplies multiplication closure and
multiplication classifier congruence over $\mathsf{RatHistoryClassifier}$.
Because the scalar classifier, vector classifier, and ambient-field classifier
are all the same RatUp classifier, the congruence row repacks directly as
scalar-action stability for the reflexive $\FieldExtUp$ package.
\end{proof}

\begin{theorem}[RatUp reflexive FieldExt ledger provenance coverage]
\label{thm:fieldext-ratup-reflexive-ledger-provenance-coverage}
For the concrete package of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, the source,
pattern, classifier, stability, exactness, and ledger rows are exhausted by the
identity embedding row, the single concrete $\FieldUp(\RatUp)$ operation table,
and the self-vector-space projection over $\mathsf{RatHistoryCarrier}$. No
additional carrier, classifier, scalar-action table, or ledger source is
introduced by the reflexive $\FieldExtUp$ reading.
\end{theorem}
\begin{proof}
The identity embedding row is
\autoref{thm:fieldext-reflexive-embedding-transport}. It fixes endpoint
transport, classifier transport, and operation transport to the unchanged
RatUp carrier and classifier.

The field and operation-table rows are supplied by
\autoref{thm:fieldext-ratup-reflexive-operation-table-coverage}. The
scalar-action readback is
\autoref{thm:fieldext-ratup-reflexive-scalar-action-readback}, so the
vector-space scalar action uses exactly the multiplication row already present
in the concrete FieldUp table.

Finally apply \autoref{thm:fieldext-reflexive-vector-space-package} and
\autoref{thm:fieldext-reflexive-certificate-obligations}. These package the
self-vector-space projection, exact endpoint classification, and ledger
provenance as the displayed $\FieldExtUp$ $\NameCert$ obligations. Hence every
ledger row named by the reflexive FieldExt certificate is traced to the
identity embedding, the RatUp FieldUp certificate, or the self-vector-space
projection.
\end{proof}

\begin{definition}[RatUp reflexive exactness and ledger interface]
\label{def:fieldext-reflexive-exactness-ledger-interface}
For the concrete data of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, the
$\FieldExtUp$ exactness and ledger surface is fixed by the single RatUp
history source. The base-field carrier, ambient-field carrier, vector
carrier, and scalar carrier are all $\mathsf{RatHistoryCarrier}$, and all
endpoint comparisons use $\mathsf{RatHistoryClassifier}$.

The embedding row is the identity map
$\iota_{\mathsf{Rat}}(h):=h$. The base and ambient field operation rows are
the rows of the concrete $\FieldUp(\RatUp)$ table, and the scalar action is
the same table read through multiplication:
$$
r\cdot_{\mathsf{Rat}} m :=
\mathsf{RatUpFieldMul}(r,m).
$$
Thus the ledger has no separate extension source: it consists of the RatUp
FieldUp operation table, the identity embedding row, and the self
vector-space row over the same classifier.
\end{definition}

\begin{theorem}[RatUp reflexive exact endpoint classification]
\label{thm:fieldext-reflexive-exact-endpoint-classification}
For the concrete data of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, every displayed
base-field endpoint, ambient-field endpoint, identity-embedding endpoint,
and scalar-action endpoint is classified by
$\mathsf{RatHistoryClassifier}$ against the RatUp endpoint named by the
same concrete operation row. In particular, the reflexive extension has one
exact classifier surface for field operations, embedding transport, and
self scalar action.
\end{theorem}
\begin{proof}
The base and ambient field endpoints are read from the same concrete
$\FieldUp(\RatUp)$ certificate. Apply
Theorem~\ref{thm:ratup-fieldup-assembled-certificate-boundary} to obtain the
operation-table rows over $\mathsf{RatHistoryCarrier}$ and
$\mathsf{RatHistoryClassifier}$.

The identity-embedding endpoints are handled by
Theorem~\ref{thm:fieldext-reflexive-embedding-transport}. Since
$\iota_{\mathsf{Rat}}$ is the identity on $\mathsf{BHist}$, the embedded
endpoint and the source endpoint are the same carried history, compared by
the RatUp classifier.

The scalar-action endpoints are handled by
Theorem~\ref{thm:fieldext-reflexive-vector-space-package}. Its scalar action
is FieldUp multiplication, so the scalar-action endpoint is classified by
the same multiplication congruence and endpoint row already present in the
RatUp FieldUp certificate.
\end{proof}

\begin{theorem}[RatUp reflexive ledger provenance]
\label{thm:fieldext-reflexive-ledger-provenance}
For the concrete data of
Definition~\ref{def:fieldext-reflexive-extension-carrier}, every
$\FieldExtUp$ ledger row is inherited from one of three displayed sources:
the single RatUp $\FieldUp$ operation table, the identity embedding row
$\iota_{\mathsf{Rat}}$, or the self-vector-space row whose scalar action is
RatUp multiplication. No ledger row uses a carrier, classifier, operation
endpoint, or scalar-action endpoint outside
$\mathsf{RatHistoryCarrier}$ and $\mathsf{RatHistoryClassifier}$.
\end{theorem}
\begin{proof}
The operation-table provenance is the concrete RatUp FieldUp certificate of
Theorem~\ref{thm:ratup-fieldup-assembled-certificate-boundary}. The base
field and ambient field read that certificate with identical carrier,
classifier, and operation endpoints.

The embedding provenance is
Theorem~\ref{thm:fieldext-reflexive-embedding-transport}. It supplies the
identity carrier row, the identity classifier row, and the preservation of
the displayed field operations without adding a second source.

The self-vector-space provenance is
Theorem~\ref{thm:fieldext-reflexive-vector-space-package}. It uses the
FieldUp additive rows for vector addition, zero, and negation, and uses the
FieldUp multiplication row as scalar action. These are exactly the remaining
ledger rows required by the reflexive $\FieldExtUp$ package.
\end{proof}

\begin{theorem}[RatUp reflexive public NameCert interface]
\label{thm:fieldext-reflexive-public-namecert-interface}
The RatUp reflexive construction exposes the public paper-side
$\FieldExtUp$ $\NameCert$ interface with carrier
$\mathsf{RatHistoryCarrier}$, classifier
$\mathsf{RatHistoryClassifier}$, identity embedding
$\iota_{\mathsf{Rat}}$, base and ambient $\FieldUp(\RatUp)$ certificates,
self-vector-space rows, exact endpoint classification, and ledger
provenance over the RatUp operation table.
\end{theorem}
\begin{proof}
The carrier and classifier are fixed by
Definition~\ref{def:fieldext-reflexive-extension-carrier}. The base and
ambient field certificates are the two readings of
Theorem~\ref{thm:ratup-fieldup-assembled-certificate-boundary}.

The stability component is supplied by
Theorem~\ref{thm:fieldext-reflexive-embedding-transport}, and the
vector-space component is supplied by
Theorem~\ref{thm:fieldext-reflexive-vector-space-package}. Together they
give the identity embedding and self scalar-action surface.

The exactness and ledger interface is
Definition~\ref{def:fieldext-reflexive-exactness-ledger-interface}. Its two
coverage theorems,
Theorems~\ref{thm:fieldext-reflexive-exact-endpoint-classification} and
\ref{thm:fieldext-reflexive-ledger-provenance}, assemble the remaining
public rows into the displayed $\FieldExtUp$ $\NameCert$ interface.
\end{proof}

\begin{theorem}[Singleton field extension as a vector space over its base]
\label{thm:fieldext-singleton-vector-space-over-base}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the extension
carrier read as $\mathsf{VecSpaceSingletonCarrier}$ with scalar action
$\mathsf{VecSpaceSingletonSmul}$ satisfies the $\VecSpaceUp$ row over the base
$\FieldUp$ source. Moreover, for every base scalar $r:\mathsf{BHist}$ and
extension vector endpoint $m:\mathsf{BHist}$ carried by
$\mathsf{VecSpaceSingletonCarrier}$, scalar multiplication by the embedded
scalar agrees, up to the singleton classifier, with singleton field
multiplication in the extension field.
\end{theorem}
\begin{proof}
The vector-space rows are exactly
Theorem~\ref{thm:singleton-empty-history-vecspace-laws}, applied to the same
scalar carrier, vector carrier, and classifier displayed in
Definition~\ref{def:fieldext-singleton-empty-history-instance}. Its semantic
certificate packaging is recorded by
Theorem~\ref{thm:singleton-empty-history-vecspace-semantic-certificate}.

The scalar-action endpoint collapses to $\emp$ by
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse}. The
extension-field multiplication endpoint also collapses to $\emp$ by
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}.

Since both endpoints are carried by $A_{\emp}$ and identified with the same
empty-history endpoint, the classifier $\rho_{\emp}$ relates the scalar-action
endpoint to the extension-field multiplication endpoint. This gives the
compatibility of embedded scalar multiplication with the singleton extension
field product.
\end{proof}
\leanchecked{BEDC.Derived.FieldExtUp.FieldExtSingletonVectorSpace\_smul\_mul\_compatible}

\begin{theorem}[Singleton FieldExt embedded scalar-action collapse]
\label{thm:fieldext-singleton-embedded-scalar-action-collapse}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, let
$r,m:\mathsf{BHist}$ be carried by $A_{\emp}$. The vector-space scalar action of
the embedded singleton scalar $\iota_{\emp}(r)$ on $m$ and the singleton
extension-field multiplication endpoint for $r$ and $m$ lie in the same
$\rho_{\emp}$ class.
\end{theorem}
\begin{proof}
Apply Theorem~\ref{thm:fieldext-singleton-vector-space-over-base}. It gives
the semantic compatibility statement between embedded scalar multiplication and
extension-field multiplication for carried scalar and vector endpoints.

The vector-space action endpoint collapses to $\emp$ by
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse}. The
extension-field multiplication endpoint collapses to $\emp$ by
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}.

Since both endpoints are carried by $A_{\emp}$ and both collapse to the same
empty-history endpoint, the shared classifier $\rho_{\emp}$ relates them.
\end{proof}

\begin{definition}[Singleton field-extension ledger policy]
\label{def:fieldext-singleton-ledger-policy}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the endpoint
ledger records exactly the base carrier $A_{\emp}$, the extension carrier
$A_{\emp}$, the vector carrier $A_{\emp}$, the identity embedding
$\iota_{\emp}(h):=h$, the singleton field operations on the base and
extension fields, the singleton vector action over the base field, and
empty-history endpoint provenance for each displayed row.

The ledger classifier attached to every carrier, embedding, field-operation,
and vector-action endpoint is the concrete classifier
$$
\rho_{\emp}(h,k):=
A_{\emp}(h)\land A_{\emp}(k)\land\hsame(h,k).
$$
No additional endpoint object is recorded by the singleton field-extension
certificate.
\end{definition}

\begin{theorem}[Singleton field-extension carrier coincidence]
\label{thm:fieldext-singleton-carrier-coincidence}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance} and the ledger
policy of Definition~\ref{def:fieldext-singleton-ledger-policy}, the base
field carrier, extension field carrier, and vector carrier are all
$A_{\emp}$. The embedding $\iota_{\emp}$ preserves and reflects carrier
membership:
$$
A_{\emp}(h)
\quad\text{if and only if}\quad
A_{\emp}(\iota_{\emp}(h)).
$$
Every displayed classifier in the field-extension certificate is the concrete
$\rho_{\emp}$ classifier.
\end{theorem}
\begin{proof}
Unfold the concrete carrier definition and the ledger policy. The three carrier
slots are all assigned the same singleton predicate $A_{\emp}$, so the carrier
coincidence is definitional.

The embedding is the identity on histories. Hence preserving and reflecting
carrier membership both reduce to the same assertion $A_{\emp}(h)$.

The classifier rows are the rows already used by
Theorem~\ref{thm:fieldext-singleton-embedding-obligations} and
Theorem~\ref{thm:fieldext-singleton-vector-space-over-base}. Each row is
displayed with the same concrete predicate $\rho_{\emp}$, so no transport
across distinct classifiers is required.
\end{proof}

\begin{theorem}[Singleton identity field-extension tower composition]
\label{thm:fieldext-singleton-identity-tower-composition}
Compose two copies of the singleton field-extension certificate of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, both governed
by the ledger policy of Definition~\ref{def:fieldext-singleton-ledger-policy}.
The composite tower again has base carrier $A_{\emp}$, middle carrier
$A_{\emp}$, top carrier $A_{\emp}$, identity composite embedding
$\iota_{\emp}\circ\iota_{\emp}=\iota_{\emp}$, singleton field-operation rows,
and the same singleton vector-space-over-base scalar action. All embedding and
scalar-action rows in the composite tower are classified by $\rho_{\emp}$.
\end{theorem}
\begin{proof}
The embedding part follows from
Theorem~\ref{thm:fieldext-singleton-embedding-obligations}. Since both
embeddings are the identity on $\mathsf{BHist}$, their composite is again the
identity embedding $\iota_{\emp}$.

The field-operation rows in the base, middle, and top fields collapse to the
same singleton endpoint by
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}. Thus tower
composition introduces no field endpoint beyond the empty-history endpoint.

The scalar-action rows are supplied by
Theorem~\ref{thm:fieldext-singleton-vector-space-over-base}. The endpoint
collapse for the singleton vector action is exactly
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse}, so the
composite tower keeps the same $\rho_{\emp}$ classifier on its action rows.
\end{proof}

\begin{theorem}[Singleton field-extension exact endpoint ledger]
\label{thm:fieldext-singleton-exact-endpoint-ledger}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance} and the ledger
policy of Definition~\ref{def:fieldext-singleton-ledger-policy}, every
embedding endpoint, every extension-field operation endpoint, and every
vector-space-over-base action endpoint recorded in the ledger collapses to the
empty history $\emp$ and is classified by $\rho_{\emp}$.
\end{theorem}
\begin{proof}
For embedding endpoints, apply
Theorem~\ref{thm:fieldext-singleton-embedding-obligations}. The embedding is
the identity, so the only carried endpoint is the same singleton history
already classified by $\rho_{\emp}$.

For extension-field operation endpoints, apply
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}. The zero,
one, addition, negation, multiplication, and proof-indexed inverse rows all
collapse to $\emp$ in the singleton field table.

For vector-space-over-base action endpoints, use
Theorem~\ref{thm:fieldext-singleton-vector-space-over-base} together with
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse}. The
scalar action collapses to the same empty-history endpoint as the compatible
extension-field multiplication row.

The ledger policy records no further endpoint kind. Therefore every recorded
endpoint row in the singleton field-extension certificate is exact at $\emp$
and classified by $\rho_{\emp}$.
\end{proof}

\begin{theorem}[Singleton field-extension certificate obligation package]
\label{thm:fieldext-singleton-certificate-obligation-package}
The concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance} assemble the
paper-side $\FieldExtUp$ obligation package: base field source, extension
field source, embedding stability and exactness, vector-space-over-base row,
exact endpoint classification, and inherited ledger provenance.
\end{theorem}
\begin{proof}
The source field certificate and extension field certificate are both supplied
by Theorem~\ref{thm:singleton-empty-history-field-schema-certificate}, because
the base and extension field carriers are the same singleton field package.

Embedding stability is supplied by
Theorem~\ref{thm:fieldext-singleton-embedding-obligations}. It records carrier
preservation, classifier preservation, and preservation of the singleton field
operations up to $\mathsf{FieldSingletonClassifier}$. Exactness is the same
identity-on-$\mathsf{BHist}$ fact: every carried base endpoint is already the
extension endpoint named by $\iota_{\emp}$.

Vector-space-over-base compatibility is supplied by
Theorem~\ref{thm:fieldext-singleton-vector-space-over-base}, whose
vector-space component is the law package of
Theorem~\ref{thm:singleton-empty-history-vecspace-laws}. Its paper-side
semantic packaging is recorded by
Theorem~\ref{thm:singleton-empty-history-vecspace-semantic-certificate}.

Exactness and ledger provenance are supplied by
Theorems~\ref{thm:fieldext-singleton-exact-endpoint-classification} and
\ref{thm:fieldext-singleton-ledger-provenance}. These clauses assemble the
listed $\FieldExtUp$ $\NameCert$ obligations for the concrete singleton
field-extension carrier.
\end{proof}

\begin{definition}[Singleton field-extension exactness and ledger interface]
\label{def:fieldext-singleton-exactness-ledger-interface}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the
$\FieldExtUp$ exactness and ledger interface is read entirely through the
singleton carrier $A_{\emp}$ and classifier $\rho_{\emp}$. Thus the displayed
base-field carrier, extension-field carrier, identity embedding endpoint,
vector scalar-action endpoint, and extension-field multiplication endpoint
all have the same source $A_{\emp}$, and every endpoint comparison used by
the certificate is a $\rho_{\emp}$ row over that source.
\end{definition}

\begin{theorem}[Singleton field-extension exact endpoint classification]
\label{thm:fieldext-singleton-exact-endpoint-classification}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, every displayed
base-field operation endpoint, every displayed extension-field operation
endpoint, the vector scalar-action endpoint, and the identity embedding
endpoint are carried by $A_{\emp}$ and classified with $\emp$ by
$\rho_{\emp}$. In particular, the operation table of the base field, the
operation table of the extension field, and the scalar-action table of the
extension vector space have one exact endpoint class.
\end{theorem}
\begin{proof}
For the base and extension field operation endpoints, apply
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}. Both
field structures in
Definition~\ref{def:fieldext-singleton-empty-history-instance} use the same
singleton $\FieldUp$ operation table.

For the vector scalar-action endpoint, apply
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse}. Its
scalar-action clause reads the endpoint as $\emp$ over the same
$A_{\emp}$ and $\rho_{\emp}$.

The embedding endpoint is immediate from $\iota_{\emp}(h):=h$. If $h$ is
carried by $A_{\emp}$, then the singleton carrier identifies $h$ with
$\emp$, and unfolding $\rho_{\emp}$ gives the displayed classifier row.
\end{proof}

\begin{theorem}[Singleton field-extension ledger provenance]
\label{thm:fieldext-singleton-ledger-provenance}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the
$\FieldExtUp$ ledger records only the identity embedding row together with
the singleton field and vector-space provenance rows. The field rows are the
two copies of the singleton empty-history field certificate, the vector row is
the singleton empty-history vector-space semantic certificate, and the
embedding row is the identity stability package for $\iota_{\emp}$.
\end{theorem}
\begin{proof}
The two field ledger rows are supplied by
Theorem~\ref{thm:singleton-empty-history-field-schema-certificate}, once for
the base field and once for the extension field. The two uses have identical
carrier, classifier, and singleton operation endpoints.

The vector-space provenance row is supplied by
Theorem~\ref{thm:singleton-empty-history-vecspace-semantic-certificate}. It
uses the same scalar source, vector source, classifier, and empty-history
scalar-action endpoint as the displayed $\FieldExtUp$ data.

The embedding row is supplied by
Theorem~\ref{thm:fieldext-singleton-embedding-obligations}. Since
$\iota_{\emp}$ is the identity on histories, no additional ledger source is
introduced beyond the singleton field and vector-space rows.
\end{proof}

\begin{theorem}[Singleton field-extension certificate projections]
\label{thm:fieldext-singleton-certificate-projections}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the
$\FieldExtUp$ certificate has the following three projections over the shared
singleton carrier $A_{\emp}$ and classifier $\rho_{\emp}$:
\begin{enumerate}
  \item its source-field projection is the singleton $\FieldUp$
  certificate on $A_{\emp}$;
  \item its extension-field projection is the singleton $\FieldUp$
  certificate on the same $A_{\emp}$;
  \item its vector-space projection is the singleton $\VecSpaceUp$-over-base
  certificate whose scalar carrier, vector carrier, and endpoint classifier
  are again $A_{\emp}$ and $\rho_{\emp}$.
\end{enumerate}
The embedding row connecting the first two projections is the identity map
$\iota_{\emp}(h):=h$.
\end{theorem}
\begin{proof}
The source and extension projections use the same displayed singleton field
data. Apply
Theorem~\ref{thm:singleton-empty-history-field-schema-certificate} once for
the source field and once for the extension field.

The vector-space projection is the semantic singleton vector-space package.
Apply Theorem~\ref{thm:singleton-empty-history-vecspace-semantic-certificate}
with the scalar carrier, vector carrier, and classifier specified in
Definition~\ref{def:fieldext-singleton-empty-history-instance}.

The projection map from the source field into the extension field is
$\iota_{\emp}$. By its definition, it is the identity on histories, so it
preserves the displayed carrier and classifier rows without introducing a
second endpoint choice.
\end{proof}

\begin{theorem}[Singleton field-extension operation readback exactness]
\label{thm:fieldext-singleton-operation-readback-exactness}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, every zero, one,
addition, negation, multiplication, proof-indexed inverse, and scalar-action
endpoint in the singleton field-extension package reads back to the singleton
empty-history endpoint. Each such endpoint is classified by $\rho_{\emp}$
against the corresponding embedded source-field endpoint or extension-field
endpoint displayed by the $\FieldExtUp$ package.
\end{theorem}
\begin{proof}
For the field operations, apply
Theorem~\ref{thm:field-singleton-concrete-operation-table-collapse}. It
collapses zero, one, addition, negation, multiplication, and the
proof-indexed inverse endpoint to the singleton empty-history endpoint.

The embedding comparison is supplied by
Theorem~\ref{thm:fieldext-singleton-embedding-obligations}. Since the embedding is
the identity on histories, the embedded source endpoint and the corresponding
extension-field endpoint are compared by the same classifier
$\rho_{\emp}$.

For scalar action, apply
Theorem~\ref{thm:singleton-empty-history-vecspace-endpoint-collapse} to read
the vector-space action endpoint as the singleton empty-history endpoint.
Then apply
Theorem~\ref{thm:fieldext-singleton-vector-space-over-base} to identify
that scalar-action endpoint with the matching extension-field multiplication
endpoint up to $\rho_{\emp}$.
\end{proof}

\begin{theorem}[Singleton field-extension nonzero domain absurdity]
\label{thm:fieldext-singleton-nonzero-domain-absurd}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, no base-field
or extension-field proof-indexed inverse domain is inhabited. Equivalently,
if $a:\mathsf{BHist}$ is carried by the singleton field carrier and
$\mathsf{FieldSingletonNonZero}(a)$ is the displayed nonzero premise used by
the base or extension field inverse row, then contradiction follows from the
singleton carrier collapse of $a$ to $\emp$.
\end{theorem}
\begin{proof}
Unfold the concrete singleton nonzero predicate. Its witness simultaneously
places $a$ at the empty history endpoint and at the endpoint
$\mathsf{e0}(\emp)$.

The singleton carrier clause supplies the collapse of the same history to
$\emp$. Composing the two endpoint identifications gives
$\emp \sim \mathsf{e0}(\emp)$ in the history classifier.

This is impossible by the constructor no-confusion principle for $\mathsf{BHist}$:
the empty history constructor and the one-step empty-marker constructor are
distinct. Hence the assumed nonzero proof parameter has no inhabitant, both
for the source field and for the extension field, because those two projected
fields use the same singleton carrier and the same singleton nonzero
predicate.
\end{proof}

\begin{theorem}[Singleton field-extension inverse-row vacuous exactness]
\label{thm:fieldext-singleton-inverse-row-vacuous-exactness}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, every
proof-indexed inverse obligation in the source field and in the extension
field is exact. The exactness is vacuous: before any inverse endpoint can be
chosen, its nonzero proof parameter belongs to the empty domain identified in
Theorem~\ref{thm:fieldext-singleton-nonzero-domain-absurd}.
\end{theorem}
\begin{proof}
Fix any displayed inverse obligation in either projected singleton field. Its
input consists of a history $a$ together with a proof that
$\mathsf{FieldSingletonNonZero}(a)$ holds.

Apply Theorem~\ref{thm:fieldext-singleton-nonzero-domain-absurd} to that proof
parameter. The resulting contradiction closes the obligation immediately, so
no separate endpoint case for inverse evaluation remains.

The same argument covers the base and extension projections because
Definition~\ref{def:fieldext-singleton-empty-history-instance} gives them the
same singleton field data. Thus every proof-indexed inverse source,
stability, and exactness row is exact over an empty domain.
\end{proof}

\begin{theorem}[Singleton field-extension inverse ledger coverage]
\label{thm:fieldext-singleton-inverse-ledger-coverage}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, the inverse
rows in the $\FieldExtUp$ source, stability, exactness, and ledger fields are
covered by the same empty-domain class. They introduce no endpoint beyond the
singleton field operation table already used for the zero, one, addition,
negation, and multiplication rows.
\end{theorem}
\begin{proof}
The source and extension inverse rows first reduce to their proof-indexed
nonzero premises. By
Theorem~\ref{thm:fieldext-singleton-inverse-row-vacuous-exactness}, those
premises are uninhabited, so the corresponding inverse obligations are exact
without selecting a new endpoint.

For the remaining operation rows, apply
Theorem~\ref{thm:fieldext-singleton-operation-readback-exactness}. It assigns
all displayed field endpoints to the singleton empty-history operation table
and compares them by $\rho_{\emp}$.

Finally combine this empty-domain inverse class with
Theorem~\ref{thm:fieldext-singleton-exactness-ledger-coverage}. The ledger
coverage therefore contains the identity embedding row, the singleton field
operation table row, the singleton vector-space scalar-action row, and no
additional inverse endpoint class.
\end{proof}

\begin{theorem}[Singleton field-extension exactness and ledger coverage]
\label{thm:fieldext-singleton-exactness-ledger-coverage}
For the concrete data of
Definition~\ref{def:fieldext-singleton-empty-history-instance}, every
$\FieldExtUp$ source row, pattern row, classifier row, stability row,
exactness row, and ledger row is covered by exactly one of the following
provenance classes: the identity embedding row, the singleton field operation
table row, or the singleton vector-space scalar-action row.
\end{theorem}
\begin{proof}
First take the projected certificate rows from
Theorem~\ref{thm:fieldext-singleton-certificate-projections}. These account
for the source-field, extension-field, and vector-space certificate surfaces
over the common $A_{\emp}$ and $\rho_{\emp}$.

Next use
Theorem~\ref{thm:fieldext-singleton-operation-readback-exactness}. It assigns
the field operation endpoints to the singleton field operation table row and
the scalar-action endpoints to the singleton vector-space scalar-action row,
with all endpoint comparisons made by $\rho_{\emp}$.

It remains to account for the cross-carrier rows. The identity embedding row
from Definition~\ref{def:fieldext-singleton-empty-history-instance} and
Theorem~\ref{thm:fieldext-singleton-embedding-obligations} covers carrier
preservation, classifier preservation, and embedded source-operation
stability.

Finally apply
Theorem~\ref{thm:fieldext-singleton-certificate-obligation-package}. Its assembled
$\FieldExtUp$ $\NameCert$ obligation list is precisely the union of these
three provenance classes, so the source, pattern, classifier, stability,
exactness, and ledger rows are all covered.
\end{proof}
