\chapter{A Concrete Naming Certificate for $\LocatedApartnessUp$}
\label{ch:concrete-instances-located-apartness-namecert}
\origin{human}

The $\LocatedApartnessUp$ packet is the Bishop--Bridges constructive-analysis
handoff from located real data to positive apartness evidence. It sits between
\autoref{ch:concrete-instances-locatedreal-namecert},
\autoref{ch:concrete-instances-apartnessreal-namecert},
\autoref{ch:concrete-instances-streamname-namecert},
\autoref{ch:concrete-instances-regseqrat-namecert},
\autoref{ch:concrete-instances-dyadicratcore-namecert}, and
\autoref{ch:concrete-instances-real-namecert}: the located endpoints supply
finite windows and dyadic enclosures, and the apartness side receives only a
positive finite gap row with visible BEDC provenance.

\begin{definition}[LocatedApartness carrier]
\label{def:located-apartness-carrier}
A $\LocatedApartnessUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
K=(L_0,L_1,S,R_0,R_1,D,G,A,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $L_0$ and $L_1$ are two accepted $\LocatedRealUp$ source rows;
\item $S$ is a shared $\StreamNameUp$ finite-window row on which both sources
are read;
\item $R_0$ and $R_1$ are the $\RegSeqRatUp$ readbacks of the two located
sources over the shared window;
\item $D$ is the pair of $\DyadicRatCoreUp$ endpoint ledgers projected from
the two located packets;
\item $G$ is a positive $\DyadicRatCoreUp$ gap row witnessing that the two
projected endpoint ledgers are disjoint on the displayed window;
\item $A$ is the $\ApartnessRealUp$ finite-window separation ledger receiving
the endpoint rows, the positive gap row, the shared window, and the two
readbacks;
\item $H$ records componentwise $\hsame$ transport for the two located sources,
the shared window, the readbacks, the dyadic endpoint ledgers, the positive gap
row, and the apartness ledger;
\item $C$ records the displayed $\Cont$ routes from located windows to
regular-rational readbacks, dyadic endpoint rows, and the apartness ledger;
\item $P$ is the $\Pkg$ provenance row over $\LocatedRealUp$,
$\ApartnessRealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$,
$\RealUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\LocatedApartnessUp}$ row.
\end{enumerate}
The classifier compares two carriers by transporting all listed rows
componentwise and then requiring that the transported positive gap row repacks
to the transported $\ApartnessRealUp$ finite-window separation ledger. No
coordinate stores trichotomy, a total order, a quotient representative, a
selected limit, completeness, or host real equality.
\end{definition}

\begin{theorem}[LocatedApartness NameCert obligation surface]
\label{thm:located-apartness-namecert-obligation-surface}
The local $\NameCert_{\LocatedApartnessUp}$ surface consists exactly of five
rows:
\begin{enumerate}
\item carrier visibility: the packet of
\autoref{def:located-apartness-carrier} displays both $\LocatedRealUp$ source
rows, the shared $\StreamNameUp$ window, the $\RegSeqRatUp$ readbacks, the
$\DyadicRatCoreUp$ endpoint ledgers, the positive gap row, and the
$\ApartnessRealUp$ ledger;
\item classifier transport: accepted packets compare only by componentwise
$\hsame$ transport and displayed $\Cont$ replay of those same rows;
\item gap-row stability: the positive $\DyadicRatCoreUp$ gap row remains
attached to the transported endpoint ledgers and the transported shared
window;
\item ledger exactness: the apartness ledger is exactly the finite-window
separation row determined by the two endpoint rows, the positive gap, the
shared window, and the two readbacks;
\item no-trichotomy and no-quotient boundary: the packet exports no classical
trichotomy, total order, quotient real representative, selected limit,
completion datum, or host equality row.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.LocatedApartnessUp.LocatedApartnessTasteGate\_single\_carrier\_alignment}
\begin{proof}
Project the carrier through \autoref{def:located-apartness-carrier}. The first
row exposes both located sources, and the next four rows expose the common
finite window, the two regular-rational readbacks, the dyadic endpoint
ledgers, and the positive gap row.

Classifier transport is componentwise. The $\hsame$ and $\Cont$ rows move the
two located packets, the shared window, the readbacks, the endpoint ledgers,
and the positive gap together, so the transported packet has the same visible
shape.

Gap-row stability and ledger exactness are then the same check at the
apartness boundary: the transported positive gap is attached to the transported
endpoint ledgers and repacked as the $\ApartnessRealUp$ finite-window
separation ledger.

The remaining boundary is negative. Since the carrier contains no coordinate
for trichotomy, total order, quotient representatives, selected limits,
completion, or host equality, no NameCert row can export any of those data.
\end{proof}

\begin{theorem}[LocatedApartness gap handoff]
\label{thm:located-apartness-gap-handoff}
Let $L_0$ and $L_1$ be transported $\LocatedRealUp$ packets over a shared
$\StreamNameUp$ finite window. If their $\RegSeqRatUp$ readbacks and
$\DyadicRatCoreUp$ endpoint ledgers display a positive dyadic gap row on that
window, then the two endpoint rows, the positive gap, the shared window, the
two readbacks, and the visible provenance repack as an $\ApartnessRealUp$
finite-window separation row.

Consequently the located pair crosses the L10 handoff as finite positive-gap
evidence, not as trichotomy of constructive reals, a total order, a quotient
real comparison, a selected representative, or a completion principle.
\end{theorem}
\begin{proof}
Project $L_0$ and $L_1$ through the $\LocatedRealUp$ carrier surface. The
projection exposes their regular-rational source rows, their finite schedules,
their dyadic endpoint ledgers, and the provenance rows used to read those data.

Use the transported shared $\StreamNameUp$ window to align the two projections.
The two $\RegSeqRatUp$ readbacks now live over the same finite observation
surface, and the dyadic endpoint rows are the endpoint ledgers displayed by the
two located packets.

Attach the positive $\DyadicRatCoreUp$ gap row to these aligned endpoint
ledgers. This forms the tuple named in the $\ApartnessRealUp$ finite-window
separation row: two endpoint rows, one positive radius or gap row, one shared
window, two readbacks, and the visible separation ledger.

Repack that tuple as the apartness ledger coordinate $A$ of
\autoref{def:located-apartness-carrier}. The repacking uses only the displayed
$\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$
provenance, so no excluded classical or quotient datum enters the handoff.
\end{proof}

\begin{closurestatus}{\LocatedApartnessUp}
  \constructivestory{A $\LocatedApartnessUp$ packet is generated from two located real source rows, a shared finite observation window, two regular-rational readbacks, dyadic endpoint ledgers, one positive dyadic gap row, an apartness separation ledger, componentwise transport, displayed continuation routes, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:located-apartness-carrier}, \autoref{thm:located-apartness-namecert-obligation-surface}, and \autoref{thm:located-apartness-gap-handoff} name the seed carrier, obligation rows, and finite positive-gap handoff between located real packets and apartness evidence.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim trichotomy of constructive reals, total order, quotient real representatives, selected limits, completeness, or a standard bridge.}
  \upgradepath{To reach obligationClosure, the carrier, five obligation rows, and gap handoff must be checked as finite BEDC packet obligations.}
\end{closurestatus}
