\chapter{A Concrete Naming Certificate for $\BolzanoWeierstrassUp$}
\label{ch:concrete-instances-bolzanoweierstrass-namecert}
\origin{human}

Following Bolzano and Weierstrass, the $\BolzanoWeierstrassUp$ packet records the finite interval-net and regular-subsequence route for a bounded $\RealUp$ sequence. The construction reads boundedness through the finite mesh surface of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}, the interval modulus surface of \autoref{ch:concrete-instances-closed-bounded-interval-uniform-modulus-namecert}, the monotone-cofinal extraction row of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert}, the regular rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, and the completed real-name seal of \autoref{ch:concrete-instances-real-namecert}. It is a subsequence compactness certificate for bounded real sequences, not an open-cover compactness theorem, a host completeness principle, quotient equality of streams, or a choice of arbitrary subsequences.

\begin{definition}[Bolzano--Weierstrass carrier]
\label{def:bolzano-weierstrass-carrier}
A $\BolzanoWeierstrassUp$ carrier is a finite $\BHist$ packet
$$
B=(S,K,R,Q,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the bounded $\RealUp$ sequence surface, exposed by finite $\StreamNameUp$ windows and bounded by the interval read used by $K$;
\item $K$ is the $\ClosedBoundedIntervalNetUp$ packet naming the finite interval nets and dyadic mesh rows used to trap subsequence windows;
\item $R$ is the $\RegularCauchySubsequenceUp$ extraction row, including the monotone-cofinal unary reindexing ledger and the selected finite windows;
\item $Q$ is the $\RegSeqRatUp$ readback row attached to the extracted windows and their dyadic tolerance comparisons;
\item $E$ is the $\RealUp$ cluster seal reached only after $S,K,R,Q$ have been displayed;
\item $H$ records componentwise $\hsame$ transport for the bounded sequence rows, interval nets, extracted subsequence rows, regular rational readback, and real cluster seal;
\item $C$ records displayed $\Cont$ routes from bounded sequence inspection through finite interval nets, regular Cauchy subsequence extraction, RegSeqRat readback, and RealUp sealing;
\item $P$ is the $\Pkg$ provenance over $\BolzanoWeierstrassUp$, $\ClosedBoundedIntervalNetUp$, $\ClosedBoundedIntervalUniformModulusUp$, $\RegularCauchySubsequenceUp$, $\RegSeqRatUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\BolzanoWeierstrassUp}$ row.
\end{enumerate}
The carrier exports no open-cover compactness object, no host completeness row, no quotient equality of real names, no least cluster selector, and no choice-selected arbitrary subsequence.
\end{definition}
\leandef{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassUp}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Bolzano--Weierstrass NameCert obligations]
\label{thm:bolzano-weierstrass-namecert-obligations}
For the carrier of \autoref{def:bolzano-weierstrass-carrier}, the local $\NameCert_{\BolzanoWeierstrassUp}$ surface consists exactly of carrier admission for $B=(S,K,R,Q,E,H,C,P,N)$, bounded sequence admission through $S$, finite interval-net admission through $K$, interval-modulus compatibility with the closed bounded interval route, monotone-cofinal regular-subsequence extraction through $R$, RegSeqRat readback through $Q$, RealUp cluster sealing through $E$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\begin{proof}
Project the carrier. The bounded sequence row $S$ is visible before any cluster seal is read, and the interval-net row $K$ supplies the finite dyadic mesh and containment rows from \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}.

Read the interval compatibility next. The uniform-modulus route of \autoref{ch:concrete-instances-closed-bounded-interval-uniform-modulus-namecert} keeps the closed bounded interval data tied to displayed dyadic covers and finite radius ledgers, so the packet does not import an open-cover object or a host minimum.

The subsequence rows close the analytic surface. The extraction row $R$ is the monotone-cofinal route of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert}, while $Q$ is the regular rational readback through \autoref{ch:concrete-instances-regseqrat-namecert}; the cluster seal $E$ is then reached through the real-name boundary of \autoref{ch:concrete-instances-real-namecert}.

Finally the structural rows $H,C,P,N$ transport, replay, source, and name only these displayed rows. No additional NameCert obligation remains outside the listed finite ledger.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass finite subsequence obligations]
\label{thm:bolzano-weierstrass-finite-subsequence-obligations}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, finite subsequence extraction is an obligation over the displayed rows $S,K,R,Q,H,C,P,N$. The row $K$ supplies finite $\ClosedBoundedIntervalNetUp$ selections, the row $R$ records the $\RegularCauchySubsequenceUp$ monotone-cofinal schedule, the row $Q$ reads the selected windows through $\RegSeqRatUp$, $\StreamNameUp$, and $\DyadicRatCoreUp$, and the terminal $\RealUp$ seal remains downstream of those rows.
\end{theorem}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassCarrier\_finite\_subsequence\_obligations}
\begin{proof}
Project the carrier of \autoref{def:bolzano-weierstrass-carrier}. The bounded source $S$ and interval-net row $K$ are visible before any subsequence schedule or real cluster seal is consumed.

Apply \autoref{thm:bolzano-weierstrass-namecert-obligations}. It identifies $K$ as the finite $\ClosedBoundedIntervalNetUp$ source, $R$ as the $\RegularCauchySubsequenceUp$ extraction row, and $Q$ as the $\RegSeqRatUp$ readback row over finite stream windows and dyadic tolerances.

Transport and replay through $H$ and $C$, then source and name the same route through $P$ and $N$. The extraction therefore uses only finite interval-net selection, monotone-cofinal scheduling, regular rational readback, $\StreamNameUp$ windows, $\DyadicRatCoreUp$ tolerances, and the downstream $\RealUp$ seal; it does not claim open-cover compactness or ambient Real completeness.
\end{proof}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrass\_tagged\_fromEventFlow\_exactness}

\begin{theorem}[Bolzano--Weierstrass interval nesting route]
\label{thm:bolzano-weierstrass-interval-nesting-route}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, nested dyadic-window retention is read only through the finite $\ClosedBoundedIntervalNetUp$ row $K$ before the $\RegularCauchySubsequenceUp$ row $R$ is consumed. Later retained windows refine earlier retained windows inside the same interval-net route, and the selected windows are then exposed to $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ without importing open-cover compactness, quotient stream equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:bolzano-weierstrass-namecert-obligations}. It places finite interval-net admission through $K$ before monotone-cofinal regular-subsequence extraction through $R$ and regular rational readback through $Q$.

At each inspected depth, the retained dyadic window is a displayed child of the same $\ClosedBoundedIntervalNetUp$ route. The transport row $H$ carries the source window and interval row together, while the replay row $C$ records the containment and dyadic tolerance facts used by the next retained window.

Only after that nesting route is displayed may $R$ append the next monotone-cofinal index. The readback row $Q$ then exposes the same retained windows through $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$, so no open-cover compactness or ambient $\RealUp$ completeness row enters the route.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass RegSeqRat handoff]
\label{thm:bolzano-weierstrass-regseqrat-handoff}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, every $\RealUp$ cluster handoff factors through the $\RegSeqRatUp$ row $Q$ after finite interval selection and regular-subsequence scheduling have been displayed. The consumer route is
$$
\ClosedBoundedIntervalNetUp \longmapsto \RegularCauchySubsequenceUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp .
$$
It exports a finite regular-rational handoff, not a host completeness point, selected cluster limit, open-cover compactness theorem, or quotient equality of streams.
\end{theorem}
\begin{proof}
Use \autoref{thm:bolzano-weierstrass-finite-subsequence-obligations} to expose finite interval-net selection, the regular-subsequence schedule, and the regular rational readback before the terminal Real seal.

Then use \autoref{thm:bolzano-weierstrass-interval-nesting-route}. The retained windows form a nested dyadic route inside $K$, and the row $R$ records the monotone-cofinal schedule attached to those windows.

Now read $Q$. Its $\RegSeqRatUp$ surface receives exactly the $\StreamNameUp$ windows and $\DyadicRatCoreUp$ tolerances already displayed by $K$ and $R$. The row $E$ may be consumed only after this handoff, and $H,C,P,N$ preserve the same route.

Thus the cluster-facing output is a finite $\RegSeqRatUp$ to $\RealUp$ handoff. No ambient completeness, selected limit, open-cover compactness, or quotient stream equality is available from the carrier.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass root interval-tree obligation]
\label{thm:bolzano-weierstrass-root-interval-tree-obligation}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, the root interval-tree obligation sends every bounded real sequence read through the finite $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ route
$$
\DyadicRatCoreUp,\ \StreamNameUp,\ \RegSeqRatUp,\ \RealUp,\ S,K,H,C,P,N .
$$
The row $S$ supplies finite $\StreamNameUp$ windows for the bounded source, $K$ supplies the dyadic interval-tree and $\DyadicRatCoreUp$ mesh rows, and $H,C,P,N$ transport, replay, source, and name only that displayed tree. The obligation refuses selected subsequence choice, open-cover compactness, quotient real equality, and ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassCarrier\_root\_interval\_tree\_obligation}
\begin{proof}
Project the carrier of \autoref{def:bolzano-weierstrass-carrier}. The bounded source row $S$ and the interval-net row $K$ are visible before any subsequence extraction or Real seal is consumed.

Apply \autoref{thm:bolzano-weierstrass-namecert-obligations}. It identifies $S,K,H,C,P,N$ as NameCert rows over bounded sequence admission, finite dyadic interval nets, componentwise transport, displayed replay, provenance, and local naming.

The excluded principles are absent from the carrier inventory. Since the interval tree is finite and dyadic, the root obligation is a displayed BEDC row rather than an open-cover compactness or choice-selected extraction principle.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass root subsequence extraction obligation]
\label{thm:bolzano-weierstrass-root-subsequence-extraction-obligation}
For an accepted $\BolzanoWeierstrassUp$ carrier, extracting a cofinal regular subsequence is an obligation over the displayed rows $S,K,R,Q,H,C,P,N$. The finite interval-tree row $K$ supplies retained bounded windows from $S$; the extraction row $R$ records the monotone-cofinal $\StreamNameUp$ reindexing ledger; and $Q$ reads those windows through $\RegSeqRatUp$ and $\DyadicRatCoreUp$ before any $\RealUp$ seal is exposed.

Thus the root extraction obligation has an explicit $\BHist,\hsame,\Cont,\NameCert$ surface and does not export selected subsequence choice, host compactness, quotient real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the interval-tree obligation of \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation}. It gives the bounded source windows and dyadic retained-cell rows before the extraction ledger is read.

Use the carrier row $R$ for monotone-cofinal reindexing and $Q$ for the regular rational readback. These are the only rows that can name the extracted subsequence in \autoref{def:bolzano-weierstrass-carrier}.

Finally use $H,C,P,N$ to transport, replay, source, and name the route. Because the subsequence is read from retained finite windows and regular rational schedules, no external selector or ambient completeness object is available.
\end{proof}

\begin{definition}[Bolzano--Weierstrass finite monotone-subsequence window]
\label{def:bolzano-weierstrass-monotone-subsequence-window}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, a finite monotone-subsequence window is the displayed BEDC row obtained by pairing:
\begin{enumerate}
\item the retained closed bounded interval rows of $K$, read as finite $\ClosedBoundedIntervalNetUp$ cells over the bounded source windows of $S$;
\item the monotone-cofinal reindexing ledger of $R$, read as the $\RegularCauchySubsequenceUp$ schedule that keeps the retained rows in increasing subsequence order;
\item the $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ readback rows of $Q$ attached to the same retained windows;
\item the transport, replay, provenance, and local naming rows $H,C,P,N$.
\end{enumerate}
The window has no coordinate for a selected infinite subsequence, quotient real equality, host open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bolzano--Weierstrass monotone window regularity]
\label{thm:bolzano-weierstrass-monotone-window-regularity}
Every finite monotone-subsequence window of an accepted $\BolzanoWeierstrassUp$ carrier is a regular BEDC readback surface. Its retained interval rows are read through the same $\StreamNameUp$ schedule, $\DyadicRatCoreUp$ mesh bounds, and $\RegSeqRatUp$ rational readback that already occur in $S,K,R,Q,H,C,P,N$.

Consequently regularity is witnessed by the displayed finite windows and monotone-cofinal ledger, not by an external selector, a quotient stream, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from \autoref{def:bolzano-weierstrass-monotone-subsequence-window}. The retained interval rows come from $K$, and the only admitted order on them is the monotone-cofinal schedule recorded by $R$.

Read the retained rows through $Q$. The $\StreamNameUp$ coordinate supplies the finite window schedule, the $\DyadicRatCoreUp$ coordinate supplies the dyadic mesh and containment bounds, and the $\RegSeqRatUp$ coordinate supplies the regular rational readback.

Finally transport the same rows through $H,C,P,N$. Since every regularity datum has already been displayed before the $\RealUp$ seal is inspected, the theorem proves regularity of the finite window surface rather than a host-level subsequence choice principle.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass closed-interval cluster handoff]
\label{thm:bolzano-weierstrass-closed-interval-cluster-handoff}
For an accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, every cluster handoff to $\RealUp$ factors through a finite monotone-subsequence window. The route first reads retained $\ClosedBoundedIntervalNetUp$ rows from $K$, then the monotone-cofinal $\RegularCauchySubsequenceUp$ ledger from $R$, then the $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ readback rows from $Q$, and only then reaches the seal row $E$.

The handoff exports no open-cover compactness, selected subsequence choice, quotient real equality, or ambient $\RealUp$ completeness. It reaches $\RealUp$ only through the finite retained rows and their displayed transport, replay, provenance, and local $\NameCert$ coordinates.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation} to obtain the finite retained interval tree and bounded source windows. These rows are the only interval data exposed by $K$.

Use \autoref{thm:bolzano-weierstrass-root-subsequence-extraction-obligation} to read the monotone-cofinal schedule through $R$ and the regular rational surface through $Q$. The preceding regularity theorem identifies that surface as the finite monotone-subsequence window.

Only after these rows are displayed may the cluster row $E$ be consumed. The support rows $H,C,P,N$ preserve the same route, so the cluster handoff remains a finite closed-interval derivation surface and never becomes an open-cover or ambient-completeness assertion.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass root Real-seal obligation]
\label{thm:bolzano-weierstrass-root-real-seal-obligation}
Every $\RealUp$ cluster endpoint exposed by an accepted $\BolzanoWeierstrassUp$ carrier is routed through the root interval-tree obligation and the root subsequence extraction obligation before the seal row $E$ is read. The cluster endpoint is therefore a displayed Real seal over $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$, not a host-level completeness point.

The obligation refuses selected subsequence choice, open-cover compactness, quotient real equality, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation}. It supplies the finite dyadic retained-cell tree and bounded source windows.

Apply \autoref{thm:bolzano-weierstrass-root-subsequence-extraction-obligation}. It extracts the monotone-cofinal schedule and reads it as the $\RegSeqRatUp$ row consumed before the Real seal.

Only then read the cluster row $E$ from \autoref{def:bolzano-weierstrass-carrier}. The support rows $H,C,P,N$ preserve the same finite route, so the displayed $\RealUp$ seal cannot turn into a selected host endpoint or an ambient completeness principle.
\end{proof}
\leanchecked{BEDC.Derived.BolzanoWeierstrassUp.BolzanoWeierstrassRootRealSealObligation}

\begin{theorem}[Bolzano--Weierstrass bounded-subsequence cluster obligation]
\label{thm:bolzano-weierstrass-bounded-subsequence-cluster-obligation}
For every accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, each bounded-subsequence cluster consumer must traverse the concrete rows
$$
S,K,R,Q,E,H,C,P,N
$$
in the BEDC route through $\ClosedBoundedIntervalNetUp$, $\RegularCauchySubsequenceUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$. The source row $S$ displays bounded real-sequence windows, $K$ retains finite closed-bounded interval cells, $R$ records the monotone-cofinal subsequence ledger, $Q$ reads the retained windows as regular rational data, and $E$ is the only $\RealUp$ cluster seal exposed after those rows.

The obligation exports no selected subsequence choice, quotient real equality, open-cover compactness theorem, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bolzano-weierstrass-carrier}. The displayed rows already separate the bounded source $S$, interval-net packet $K$, extraction ledger $R$, regular readback $Q$, Real seal $E$, and structural rows $H,C,P,N$.

Apply \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation}. It places every bounded source read behind the finite $\ClosedBoundedIntervalNetUp$ route and the dyadic interval cells retained by $K$.

Apply \autoref{thm:bolzano-weierstrass-root-subsequence-extraction-obligation}. The retained windows are then consumed by $R$ as a $\RegularCauchySubsequenceUp$ schedule and by $Q$ through $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$.

Finally use \autoref{thm:bolzano-weierstrass-root-real-seal-obligation}. Since $E$ is downstream of those rows and $H,C,P,N$ only transport, replay, source, and name the same route, the bounded-subsequence cluster surface cannot expose a selected subsequence, quotient equality, open-cover compactness proof, or ambient completeness row.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster Real-seal factorization]
\label{thm:bolzano-weierstrass-cluster-real-seal-factorization}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. Every $\RealUp$ cluster seal read from $B$ factors first through the closed-bounded interval net row $K$, then through the regular Cauchy subsequence row $R$, then through the finite $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ readback surface inside $Q$, and only then through $E,H,C,P,N$.

Equivalently, the cluster seal is a displayed factorization
$$
\ClosedBoundedIntervalNetUp \longmapsto \RegularCauchySubsequenceUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RegSeqRatUp \longmapsto \RealUp
$$
over the same concrete rows $S,K,R,Q,E,H,C,P,N$. It is not a quotient-real equality witness, not an open-cover compactness principle, not a selected subsequence, and not ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:bolzano-weierstrass-bounded-subsequence-cluster-obligation}. It displays the complete carrier route and identifies the only rows available to a cluster consumer.

The interval-net part is supplied by $K$. The regular-subsequence part is supplied by $R$, whose retained windows are the same finite windows obtained from $S$ through $K$.

The readback part is supplied by $Q$. It passes the retained finite windows through $\StreamNameUp$, reads dyadic tolerances through $\DyadicRatCoreUp$, and exposes the regular rational surface through $\RegSeqRatUp$ before the cluster row $E$ can be consumed.

Rows $H,C,P,N$ preserve the displayed route by transport, replay, provenance, and local naming. Therefore the factorization reaches the $\RealUp$ seal only through the named finite rows and cannot introduce quotient real equality, selected subsequence choice, open-cover compactness, or ambient completeness.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass interval-net choice-free retention]
\label{thm:bolzano-weierstrass-interval-net-choice-free-retention}
For every accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, the retained interval windows used by the cluster route are retained inside the displayed $\ClosedBoundedIntervalNetUp$ row $K$ before the $\RegularCauchySubsequenceUp$ row $R$ is read. Each retained window is then passed through $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and the terminal $\RealUp$ seal row $E$ using only the same $S,K,R,Q,H,C,P,N$ support.

Thus interval retention is a finite NameCert projection from the carrier, not a countable-choice selection of subsequence indices, not quotient real equality, not open-cover compactness, and not an appeal to ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the finite interval tree supplied by \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation}. The row $K$ displays the closed-bounded interval net and the retained cells before any subsequence schedule is consumed.

Use \autoref{thm:bolzano-weierstrass-root-subsequence-extraction-obligation}. The row $R$ reads only the retained windows already exposed by $K$, so its monotone-cofinal schedule is a projection of the finite interval-net ledger rather than an external choice function.

Read the retained windows through $Q$ and then through $E$. The $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ rows are therefore downstream of the same retained interval data, and the Real seal is reached only after that readback.

Finally transport and name the route with $H,C,P,N$. Since no carrier row stores a choice-selected subsequence, quotient equality, open-cover compactness proof, or ambient completeness principle, the interval-net retention remains choice-free.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded sequence source]
\label{thm:bolzano-weierstrass-bounded-sequence-source}
Every accepted $\BolzanoWeierstrassUp$ carrier reads bounded $\RealUp$ sequence data through the finite source route
$$
\StreamNameUp,\quad \DyadicRatCoreUp,\quad \RegSeqRatUp,\quad \RealUp,\quad \BHist,\quad \hsame,\quad \Cont,\quad \NameCert
$$
before any interval-net row is consumed. The bounded source row $S$ exposes only scheduled stream windows, dyadic tolerance comparisons, regular rational readback, and the terminal real-name seal needed to feed $K,R,Q,E,H,C,P,N$. It does not expose selected subsequence choice, quotient real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier $B=(S,K,R,Q,E,H,C,P,N)$ from \autoref{def:bolzano-weierstrass-carrier}. The source coordinate $S$ is the only row that can supply bounded sequence observations before interval nets are opened.

Read $S$ through the displayed stream, dyadic, regular rational, and real rows. The $\StreamNameUp$ windows give finite sequence observations, $\DyadicRatCoreUp$ gives the tolerance comparisons, $\RegSeqRatUp$ gives the regular readback, and $\RealUp$ seals the bounded real-name surface.

Only after that source route is displayed may the interval-net row $K$ be consumed. The structural rows $H,C,P,N$ transport, replay, source, and name the same route, leaving no coordinate for selected subsequence choice, quotient real equality, open-cover compactness, or ambient completeness.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass interval-net obligation]
\label{thm:bolzano-weierstrass-interval-net-obligation}
For every accepted $\BolzanoWeierstrassUp$ carrier $B=(S,K,R,Q,E,H,C,P,N)$, the rows $\ClosedBoundedIntervalNetUp$ and $\ClosedBoundedIntervalUniformModulusUp$ are the only interval-tree source for retained windows. Every retained window consumed by $R$ or $Q$ must first be read through $K$ and its uniform-modulus compatibility route, and the route refuses selected subsequence choice, quotient real equality, open-cover compactness, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from the interval-net coordinate $K$. It is the only carrier row naming finite closed bounded interval nets, dyadic mesh cells, and retained windows.

The uniform-modulus compatibility is read inside the same interval-tree route. It binds the retained windows to displayed dyadic refinements and prevents a consumer from substituting an open-cover compactness proof or a host finite-subcover selector.

Rows $R$ and $Q$ consume retained windows only after $K$ has supplied them. Transport and replay through $H$ and $C$, followed by provenance and local naming through $P,N$, preserve the same interval-tree source and add no quotient real equality, selected subsequence choice, or ambient completeness coordinate.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass regular subsequence window readback]
\label{thm:bolzano-weierstrass-regular-subsequence-window-readback}
Every accepted $\BolzanoWeierstrassUp$ route consumes $\RegularCauchySubsequenceUp$ and $\RegSeqRatUp$ readback before the $\RealUp$ cluster seal. The row $R$ records the monotone-cofinal retained-window extraction from the interval tree, the row $Q$ reads those windows as regular rational data, and only then may $E$ be read as the Real cluster seal. The readback exports no selected subsequence choice, quotient real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:bolzano-weierstrass-interval-net-obligation} to obtain retained windows from $K$. These windows are finite interval-tree data rather than host subsequence choices.

Read the extraction row $R$ next. It records the monotone-cofinal $\RegularCauchySubsequenceUp$ route, so the subsequence window is named by displayed reindexing data.

Read $Q$ before $E$. The regular rational readback turns the extracted windows into the $\RegSeqRatUp$ surface consumed by the Real cluster seal, and the rows $H,C,P,N$ preserve that order.

Thus the Real seal is downstream of regular-subsequence and regular-rational readback. None of the refused principles appears in the carrier rows or in the transport and replay route.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass regular subsequence route]
\label{thm:bolzano-weierstrass-regular-subsequence-route}
Every accepted $\BolzanoWeierstrassUp$ carrier routes a bounded real sequence to a regular Cauchy subsequence through the finite path
$$
S,K,R,Q,H,C,P,N.
$$
The path first reads the bounded sequence surface $S$, then the finite interval-net packet $K$, then the monotone-cofinal extraction row $R$, and finally the $\RegSeqRatUp$ readback row $Q$. The route does not expose a choice-selected arbitrary subsequence, a quotient-stream representative, a host compactness theorem, or an ambient completeness field.
\end{theorem}
\begin{proof}
Start with the bounded sequence row. The only boundedness data visible to the carrier is the finite sequence surface $S$ together with the closed bounded interval net $K$.

Apply the interval-net route of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}. Its dyadic mesh rows supply nested finite traps for inspected sequence windows, and its Real-facing seal remains downstream of the displayed mesh and readback rows.

Now use the regular-subsequence route of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert}. The row $R$ supplies a monotone-cofinal unary reindexing ledger, so the subsequence is read by finite reindexing data rather than by an arbitrary choice function.

The row $Q$ reads the extracted windows as a $\RegSeqRatUp$ surface. Transport and replay through $H$ and $C$, followed by $P$ and $N$, preserve that same route, leaving no coordinate for quotient streams, host compactness, or ambient completeness.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded source factorization]
\label{thm:bolzano-weierstrass-bounded-source-factorization}
Every accepted $\BolzanoWeierstrassUp$ carrier reads its bounded sequence row $S$ through the finite $\BoundedRealSequenceUp$ route of \autoref{ch:concrete-instances-boundedrealsequence-namecert} before it consumes the $\ClosedBoundedIntervalNetUp$ row $K$, the $\RegularCauchySubsequenceUp$ row $R$, the $\RegSeqRatUp$ readback row $Q$, and the terminal $\RealUp$ cluster seal. Thus the bounded-source surface of the Bolzano--Weierstrass packet is not a free host-level sequence input; it is the reusable finite certificate supplied by \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}. It exposes the bounded real sequence source by the finite route $S,W,Q,R,I,H,C,P,N$, with stream windows, regular readback, a $\RealUp$ seal, and an interval-net bound row already displayed inside the $\BoundedRealSequenceUp$ certificate.

Feed that certified source into \autoref{thm:bolzano-weierstrass-regular-subsequence-route}. The Bolzano--Weierstrass carrier can then consume $K$ for closed bounded interval nets, $R$ for monotone-cofinal regular subsequence extraction, $Q$ for $\RegSeqRatUp$ readback, and the terminal $\RealUp$ seal without adding another bounded-sequence coordinate.

The composite route leaves no slot for open-cover compactness, host completeness, quotient stream equality, or a choice-selected subsequence. Those principles are not transported by the $\BoundedRealSequenceUp$ handoff, and the regular-subsequence route only consumes the displayed finite rows.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded cluster route]
\label{thm:bolzano-weierstrass-bounded-cluster-route}
Every accepted $\BolzanoWeierstrassUp$ carrier whose bounded source is supplied by $\BoundedRealSequenceUp$ and whose terminal cluster candidate is consumed by $\RealSequenceClusterPointUp$ factors through the concrete route
$$
\BoundedRealSequenceUp \longmapsto \ClosedBoundedIntervalNetUp \longmapsto \RegularCauchySubsequenceUp \longmapsto \RegSeqRatUp \longmapsto \RealSequenceClusterPointUp \longmapsto \RealUp .
$$
The same finite interval-tree evidence is preserved by the displayed $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ rows, so the cluster consumer receives no detached bounded sequence, arbitrary subsequence selector, quotient stream equality, open-cover compactness, or ambient completeness row.
\end{theorem}
\begin{proof}
Start with the bounded-source factorization of \autoref{thm:bolzano-weierstrass-bounded-source-factorization}. It places the source row $S$ behind the finite $\BoundedRealSequenceUp$ handoff of \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff} before the interval-net row $K$ is consumed.

Use the interval-tree induction and regular-Cauchy subsequence readback blocks. The row $K$ supplies the retained closed-bounded interval cells, $R$ records the monotone-cofinal $\RegularCauchySubsequenceUp$ ledger, and $Q$ reads the selected windows as $\RegSeqRatUp$ data.

Now consume the terminal cluster candidate through the public export of \autoref{thm:real-sequence-cluster-point-public-export}. The $\RealSequenceClusterPointUp$ route reads the same bounded source, cofinal subsequence, selected windows, regular readback, dyadic tolerance ledger, and $\RealUp$ seal before a cluster point is exposed.

Finally $H,C,P,N$ transport, replay, source, and name that same finite interval-tree evidence. Since no second source, selector, quotient stream, open-cover compactness theorem, or ambient completeness row is present, the bounded cluster route is exactly the displayed composite.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass finite interval-tree induction]
\label{thm:bolzano-weierstrass-finite-interval-tree-induction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. For every inspected unary depth of the closed-bounded interval net, the displayed finite dyadic refinement tree in $K$ determines, by induction on that tree, a retained cell, a nonempty finite sequence-window row from $S$, and a monotone-cofinal reindexing row in $R$. The retained cells refine through the same $\ClosedBoundedIntervalNetUp$ and $\ClosedBoundedIntervalUniformModulusUp$ rows, and the extracted finite windows are exactly the $\RegSeqRatUp$ readback consumed by $Q$.
\end{theorem}
\begin{proof}
For depth $0$, read the root bounded interval from $S$ and the root net row from $K$. The boundedness ledger supplies a nonempty inspected sequence-window row in $S$, and the identity unary index row is monotone and cofinal on the displayed root window.

For the induction step, assume the retained cell and window have been displayed at depth $d$. The dyadic mesh row in $K$ splits that cell into its finite children at depth $d+1$, and the packet ledger witnesses that at least one child retains a nonempty finite sequence-window row from $S$.

Choose that retained child only by the displayed finite branch witness. Componentwise transport through $H$ carries the previous route to the child cell, while displayed replay through $C$ records the same containment and radius facts in the $\ClosedBoundedIntervalNetUp$ and $\ClosedBoundedIntervalUniformModulusUp$ rows.

The reindexing row in $R$ appends the retained-window index and records monotonicity and cofinality in the unary ledger. Reading the selected windows through $Q$ gives precisely the regular rational schedule consumed as $\RegSeqRatUp$, so the subsequence route is derived from finite interval refinement rather than from an external selector.

No open-cover compactness, arbitrary subsequence choice, quotient stream, or host completeness row is used. The induction uses only the finite tree displayed by $K$, the inspected windows in $S$, the monotone-cofinal ledger in $R$, and the readback route in $Q$.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass regular-Cauchy subsequence readback]
\label{thm:bolzanoweierstrass-regular-cauchy-subsequence-readback}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The finite retained cells supplied by \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction} force the monotone-cofinal schedule in $R$ and the $\RegSeqRatUp$ readback in $Q$ through the displayed route
$$
\DyadicRatCoreUp \longmapsto \StreamNameUp \longmapsto \RegularCauchySubsequenceUp \longmapsto \RegSeqRatUp .
$$
Thus the regular Cauchy subsequence is read from finite interval-tree evidence and retained windows, with no selected subsequence, quotient stream representative, host compactness theorem, or ambient $\RealUp$ completeness row.
\end{theorem}
\begin{proof}
Start with the bounded source factorization of \autoref{thm:bolzano-weierstrass-bounded-source-factorization}. It ensures that the source row $S$ is already a displayed bounded real-sequence surface before the interval tree is consumed.

Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. At each inspected depth it supplies a retained cell, a nonempty finite window from $S$, and a monotone-cofinal ledger entry in $R$.

Use \autoref{thm:bolzano-weierstrass-regular-subsequence-route}. The retained finite windows are the only windows handed to the regular subsequence route, so the $\StreamNameUp$ schedule is determined by the displayed ledger rather than by an external selector.

Finally read the selected windows through $Q$. The dyadic tolerances are carried by the same interval-tree rows in $K$, the windows are the same finite $\StreamNameUp$ rows recorded by $R$, and the readback is exactly the $\RegSeqRatUp$ surface consumed by the carrier.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster Real-seal handoff]
\label{thm:bolzanoweierstrass-cluster-real-seal-handoff}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The cluster row $E$ is read only after the regular-Cauchy subsequence readback of \autoref{thm:bolzanoweierstrass-regular-cauchy-subsequence-readback}. Consequently the cluster point exported by $B$ is a displayed $\RealUp$ seal over $S,K,R,Q,H,C,P,N$, not an ambient completeness point, not a selected limit, not quotient equality, and not an open-cover compactness witness.
\end{theorem}
\begin{proof}
Begin with the root Real-seal obligation of \autoref{thm:bolzano-weierstrass-root-real-seal-obligation}. It places every $\RealUp$ cluster endpoint downstream of the root interval-tree obligation and root subsequence extraction obligation.

Apply \autoref{thm:bolzanoweierstrass-regular-cauchy-subsequence-readback}. The theorem displays the retained cells, monotone-cofinal ledger, finite stream windows, dyadic tolerances, and $\RegSeqRatUp$ readback before $E$ is consumed.

Now use \autoref{thm:bolzano-weierstrass-real-cluster-seal}. The row $E$ seals that already displayed regular Cauchy readback as a $\RealUp$ boundary, and the structural rows $H,C,P,N$ only transport, replay, source, and name the same finite route.

Therefore the cluster handoff exports a displayed Real seal and nothing stronger. The carrier contains no coordinate for ambient completeness, selected limits, quotient equality, open-cover compactness, or arbitrary subsequence choice.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass retained-cell monotonicity]
\label{thm:bolzano-weierstrass-retained-cell-monotonicity}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. If two inspected unary depths are read from the same finite closed-bounded interval net row $K$, and the second depth is later in the displayed unary order, then the retained cell at the later depth refines the retained cell at the earlier depth through the same $\ClosedBoundedIntervalNetUp$ and $\ClosedBoundedIntervalUniformModulusUp$ rows. The nonempty sequence-window row supplied by $S$ for the later depth is a displayed continuation of the earlier retained window before the monotone-cofinal reindexing row $R$ is consumed.
\end{theorem}
\begin{proof}
Induct on the finite refinement tree supplied by \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. At the root depth, the retained cell is the root closed bounded interval read from $S$ and $K$, and its nonempty inspected window is the initial window displayed by the bounded-sequence surface.

For the successor step, the induction hypothesis gives the earlier retained cell, its nonempty window, and its refinement ledger inside $K$. The finite tree row chooses a child retained cell at the later depth together with a nonempty finite sequence-window row, and the child containment is read through the same closed-bounded interval net and interval-modulus rows.

Transport the earlier route componentwise by $H$ and replay the displayed continuation by $C$. This records that the later window extends the earlier retained-window display before the ledger $R$ appends the later index. Thus the refinement relation and the sequence-window continuation are already present in the finite interval-net surface when the monotone-cofinal reindexing row is read.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cofinal window extraction]
\label{thm:bolzano-weierstrass-cofinal-window-extraction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The retained-cell nesting of \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity} supplies the nested cofinal ledger in $R$, and the selected finite sequence windows are exactly the windows handed to the $\RegSeqRatUp$ readback row $Q$. Thus the regular readback route is fixed by the retained interval-cell ledger and uses no arbitrary subsequence choice, quotient stream, host compactness, or ambient completeness row.
\end{theorem}
\begin{proof}
Project the accepted carrier through \autoref{def:bolzano-weierstrass-carrier}. The visible coordinates are the bounded sequence surface $S$, the finite interval-net packet $K$, the extraction row $R$, the readback row $Q$, and the structural rows $H,C,P,N$.

Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction} at each inspected unary depth. It supplies a retained interval cell, a nonempty finite sequence-window row from $S$, and a displayed refinement relation through $K$ and the interval-modulus route.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity} to the retained cells at successive inspected depths. Refinement in $K$ preserves the nesting of retained cells, while interval-modulus compatibility preserves the requested finite mesh bound; together these rows keep the ledger monotone and cofinal inside the displayed extraction surface.

Finally read the selected windows through $Q$. Since $Q$ is attached to the extracted windows of $R$, and $R$ was built only by appending retained finite-window indices, the $\RegSeqRatUp$ readback receives precisely those windows and no additional subsequence selector or external completeness route.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass Real cluster seal]
\label{thm:bolzano-weierstrass-real-cluster-seal}
Every $\RealUp$ cluster read from an accepted $\BolzanoWeierstrassUp$ carrier factors through
$$
S,K,R,Q,E,H,C,P,N.
$$
The cluster row $E$ is reached only after the bounded sequence surface, finite interval-net packet, cofinal-window extraction ledger, regular Cauchy subsequence extraction row, and RegSeqRat readback have been displayed. Consequently a real-facing consumer receives a finite subsequence compactness seal and receives no open-cover compactness principle, host completeness row, quotient equality of streams, least cluster selector, or choice-selected arbitrary subsequence.
\end{theorem}
\begin{proof}
Begin with the factorization in \autoref{thm:bolzano-weierstrass-regular-subsequence-route}. It displays $S,K,R,Q$ before any real cluster row can be consumed.

Then use \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The row $R$ is a monotone-cofinal ledger built from retained interval cells, and $Q$ reads exactly the selected finite sequence windows supplied by that ledger.

Use the $\RealUp$ chapter \autoref{ch:concrete-instances-real-namecert} only after that route is visible. The seal $E$ is therefore a real-name boundary for the extracted regular Cauchy readback, not a separate host limit or quotient representative.

The transport and continuation rows preserve the same finite route. Since the carrier contains no coordinate for open-cover compactness, host completeness, quotient equality, a least cluster selector, or an arbitrary subsequence choice, the rows $S,K,R,Q,E,H,C,P,N$ exhaust the cluster seal.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded window induction]
\label{thm:bolzano-weierstrass-bounded-window-induction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The bounded-window induction consumed by the packet is the finite interval-tree induction of \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction} restricted to the $\BoundedRealSequenceUp$ source row $S$ and the $\ClosedBoundedIntervalNetUp$ row $K$. At each inspected unary depth it exposes a retained closed interval cell, a nonempty bounded sequence window, and the next monotone-cofinal ledger entry before any $\RegSeqRatUp$ readback or $\RealUp$ cluster seal is consumed.
\end{theorem}
\begin{proof}
Start with the bounded source factorization. It reads the bounded $\RealUp$ sequence through the finite $\BoundedRealSequenceUp$ surface before the interval-net row is consumed.

Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. The induction step uses only the finite children displayed by $K$ and the nonempty inspected windows displayed by $S$.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. The retained cells and their bounded source windows refine along the same closed bounded interval net, so the next ledger entry in $R$ is attached to a displayed bounded window rather than to an external subsequence selector.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cofinal cluster seal]
\label{thm:bolzano-weierstrass-cofinal-cluster-seal}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier whose bounded-window induction row is displayed. The extracted cofinal windows pass through the consumer chain
$$
\RegSeqRatUp \longmapsto \StreamNameUp \longmapsto \DyadicRatCoreUp \longmapsto \RealUp
$$
using only the rows $R,Q,E,H,C,P,N$. The terminal cluster seal is therefore a $\RealUp$ boundary for the retained cofinal windows, not a quotient stream representative, selected limit, or ambient completeness point.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. It identifies the row $R$ as the monotone-cofinal ledger built from retained bounded windows and identifies $Q$ as the $\RegSeqRatUp$ readback of those windows.

Use the stream and dyadic rows already present in the carrier provenance. The same selected finite windows are read as $\StreamNameUp$ windows, and their tolerance comparisons are routed through $\DyadicRatCoreUp$ before any cluster endpoint is sealed.

Finally apply \autoref{thm:bolzano-weierstrass-real-cluster-seal}. Since $E$ is reached only after the retained windows, regular readback, stream windows, and dyadic tolerances are displayed, the cluster seal stays inside the finite cofinal route.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass ledger refusal]
\label{thm:bolzano-weierstrass-ledger-refusal}
Every accepted $\BolzanoWeierstrassUp$ carrier refuses any consumer ledger that asks for arbitrary subsequence choice, quotient stream equality, open-cover compactness, or ambient $\RealUp$ completeness. Such a ledger cannot be filled from $S,K,R,Q,E,H,C,P,N$ because those rows expose only bounded source windows, finite interval nets, monotone-cofinal reindexing, regular rational readback, a Real cluster seal, transport, replay, provenance, and local naming.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bolzano-weierstrass-carrier}. Its rows are exactly $S,K,R,Q,E,H,C,P,N$, and none of those rows is an arbitrary subsequence selector, quotient stream equality proof, open-cover compactness object, or ambient completeness theorem.

Apply \autoref{thm:bolzano-weierstrass-bounded-window-induction} and \autoref{thm:bolzano-weierstrass-cofinal-cluster-seal}. They show that every cluster-facing route is built from finite bounded windows, retained interval cells, cofinal readback, StreamName windows, DyadicRatCore tolerances, and the terminal Real seal.

The structural rows $H,C,P,N$ only transport, replay, source, and name that displayed route. Therefore a consumer ledger containing any of the excluded principles has no carrier coordinate from which its requested row could be produced.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster seal extraction]
\label{thm:bolzano-weierstrass-cluster-seal-extraction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The cluster seal $E$ is extracted only by composing the finite interval-tree induction, retained-cell monotonicity, cofinal-window extraction, and $\RegSeqRatUp$ readback route displayed by $S,K,R,Q,H,C,P,N$. The resulting consumer-facing output is a $\RealUp$ cluster seal for the displayed bounded sequence, and it exports no open-cover compactness principle, host completeness row, quotient-stream equality, least-cluster selector, or arbitrary subsequence choice.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. It supplies the retained finite interval cells, the nonempty inspected windows, and the displayed finite-branch witness that keeps the route inside the closed-bounded interval net surface.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. The retained cells form the nested refinement ledger, and the continuation rows preserve the same bounded-sequence windows through the later inspected depths.

Apply \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The ledger $R$ is monotone and cofinal, while $Q$ reads exactly the selected finite windows as the regular rational schedule consumed by $\RegSeqRatUp$.

Finally apply \autoref{thm:bolzano-weierstrass-real-cluster-seal}. The terminal row $E$ is therefore a $\RealUp$ boundary for the extracted regular Cauchy readback, so no open-cover compactness, host completeness, quotient-stream equality, least-cluster selector, or arbitrary subsequence choice is exported to the completion-facing consumer.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass tail-modulus window stability]
\label{thm:bolzano-weierstrass-tail-modulus-window-stability}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The retained interval cells selected from $K$ and their dyadic mesh moduli transport through the same $H$ and $C$ rows to the same $\RegSeqRatUp$ readback windows in $Q$. In particular, changing an accepted packet by componentwise $\hsame$ transport may rename the displayed bounded source, retained-cell ledger, and modulus rows, but it cannot change which finite source windows are read by $Q$ before the $\RealUp$ cluster seal $E$ is consumed.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. It attaches each inspected unary depth to a retained interval cell, a nonempty bounded source window from $S$, and a displayed dyadic mesh row in $K$.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. Later retained cells refine earlier cells through the same interval-net and interval-modulus rows, so the mesh modulus remains tied to the same finite refinement ledger.

Apply \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The cofinal ledger $R$ records exactly the selected source windows, and the row $Q$ reads precisely those windows as the $\RegSeqRatUp$ schedule.

The rows $H$ and $C$ transport and replay only this displayed route. Thus any accepted transported packet preserves the retained-cell modulus route and cannot redirect the regular rational readback to a different finite window surface.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass Real-seal nonescape]
\label{thm:bolzano-weierstrass-cluster-seal-real-nonescape}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The $\RealUp$ cluster seal $E$ factors only through $S,K,R,Q,E,H,C,P,N$. Hence the seal cannot export open-cover compactness, host completeness, quotient stream equality, or arbitrary subsequence choice to any Real-facing or completion-facing consumer.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-cluster-seal-extraction}. The seal is extracted by composing finite interval-tree induction, retained-cell monotonicity, cofinal window extraction, and $\RegSeqRatUp$ readback.

Apply \autoref{thm:bolzano-weierstrass-real-cluster-seal}. The row $E$ is reached only after $S,K,R,Q$ have displayed the bounded sequence surface, retained interval cells, cofinal reindexing row, and regular rational readback.

The remaining rows $H,C,P,N$ provide componentwise transport, displayed replay, provenance, and local naming for that same route. None of these rows contains an open-cover compactness object, host completeness theorem, quotient stream equality, or arbitrary subsequence selector.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cofinal-subsequence classifier exactness]
\label{thm:bolzano-weierstrass-cofinal-subsequence-classifier-exactness}
Let $B=(S,K,R,Q,E,H,C,P,N)$ and $B'=(S',K',R',Q',E',H',C',P',N')$ be accepted $\BolzanoWeierstrassUp$ carriers. Their cofinal-subsequence classifiers agree exactly when the bounded source windows, retained interval cells, cofinal reindexing rows, $\RegSeqRatUp$ readback rows, and $\RealUp$ cluster seal rows agree under the displayed $H,C,P,N$ and $H',C',P',N'$ transport. No further classifier coordinate is available outside those finite rows.
\end{theorem}
\begin{proof}
For the forward direction, read classifier agreement through \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The accepted classifier must preserve the retained source windows in $S$, the retained cells in $K$, the cofinal ledger in $R$, and the readback row $Q$.

Then apply \autoref{thm:bolzano-weierstrass-cluster-seal-extraction}. Agreement of the extracted subsequence route determines the terminal Real cluster seal row $E$ because that seal is downstream of the same finite route.

For the reverse direction, assume the listed rows agree under the displayed transports. The finite interval-tree induction and retained-cell monotonicity reconstruct the same retained-cell route, while cofinal window extraction reconstructs the same $R,Q$ readback surface.

Finally use \autoref{thm:bolzano-weierstrass-cluster-seal-real-nonescape}. Since the Real seal and structural rows exhaust the classifier surface, the two accepted packets have the same cofinal-subsequence classifier and no hidden host-level equality or choice coordinate remains.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass dyadic-mesh subsequence witness]
\label{thm:bolzano-weierstrass-dyadic-mesh-subsequence-witness}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. At every inspected unary depth, the finite closed-bounded interval net row $K$ supplies a retained dyadic cell, a nonempty finite sequence-window row from $S$, and the next monotone-cofinal subsequence index recorded by $R$. The witness is read through the displayed $\ClosedBoundedIntervalNetUp$ and $\ClosedBoundedIntervalUniformModulusUp$ rows, and it exports no open-cover compactness, quotient stream equality, arbitrary choice of subsequence, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. It reads the root interval, the finite dyadic refinements, and the nonempty inspected windows from $S$ and $K$.

At each inspected depth, use the retained-cell witness supplied by the finite tree. The construction chooses only among displayed finite children and records the chosen child as a retained dyadic cell, so the subsequence index is a row of $R$ rather than a host-level selector.

Transport and replay by $H$ and $C$ preserve the same interval-net and sequence-window rows. Since no carrier coordinate contains an open cover, quotient stream equality, arbitrary subsequence choice, or ambient completeness, the dyadic-mesh witness exports none of those principles.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded-window nonempty extraction]
\label{thm:bolzano-weierstrass-bounded-window-nonempty-extraction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. Every retained dyadic cell selected from the finite interval net $K$ carries a nonempty bounded sequence-window row from $S$, and this row is the only source from which $R$ may append the next monotone-cofinal subsequence index. The extraction therefore passes through the finite interval-tree induction, retained-cell monotonicity, and dyadic-mesh subsequence witness before any selected window is handed to $Q$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. At each inspected unary depth it supplies a retained cell together with a nonempty finite sequence-window row from $S$ and the corresponding monotone-cofinal reindexing row in $R$.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. Later retained cells refine earlier retained cells through the same interval-net rows, and the later nonempty window is a continuation of the earlier bounded window before $R$ appends the next index.

Finally apply \autoref{thm:bolzano-weierstrass-dyadic-mesh-subsequence-witness}. The witness records that the next subsequence index is attached to the retained dyadic cell and its displayed nonempty window from $S$. Since the carrier has no further source coordinate for subsequence indices, $R$ can append the next monotone-cofinal index only from that bounded window row.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster Cauchy window]
\label{thm:bolzano-weierstrass-cluster-cauchy-window}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The retained-cell nesting from $K$ yields the regular Cauchy window consumed by the $\RegSeqRatUp$ row $Q$: later retained cells refine earlier retained cells, their dyadic diameters follow the inspected unary depth, and the selected windows recorded by $R$ are exactly the finite windows read by $Q$.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. It records that retained cells at later inspected depths refine the earlier retained cells through the same closed-bounded interval-net and interval-modulus rows.

Then apply \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The monotone-cofinal ledger $R$ appends only indices attached to those retained cells, and $Q$ reads precisely the resulting finite sequence windows.

The dyadic diameter control is therefore a displayed regular Cauchy window. It is consumed by $\RegSeqRatUp$ before the Real cluster seal is read, and no quotient stream equality, arbitrary choice, or ambient completeness row is introduced.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass finite interval-subsequence exhaustion]
\label{thm:bolzano-weierstrass-finite-interval-subsequence-exhaustion}
Every accepted $\BolzanoWeierstrassUp$ packet whose bounded $\RealUp$ sequence row, closed bounded interval-net route, dyadic mesh row, regular-subsequence row, $\StreamNameUp$ windows, $\RegSeqRatUp$ readback, $\hsame$ transport, $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows are displayed exports its cluster witness only through the finite interval-tree induction route plus cofinal window extraction. In particular, the cluster route is exhausted by \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}, \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}, \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}, and \autoref{thm:bolzano-weierstrass-cluster-cauchy-window}, and it exports no arbitrary subsequence choice or host $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}. It supplies, at each inspected unary depth, the retained dyadic cell, nonempty source window, and monotone-cofinal reindexing row from the displayed interval tree.

Apply \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}. The retained cells refine through the same closed bounded interval-net route, so the later windows are continuations of the earlier finite windows rather than outputs of an external selector.

Apply \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}. The cofinal ledger in $R$ is built from those retained windows, and the $\RegSeqRatUp$ row $Q$ reads exactly that finite window surface.

Finally apply \autoref{thm:bolzano-weierstrass-cluster-cauchy-window}. The Cauchy window consumed by $Q$ is already determined by the retained-cell ledger, while $H,C,P,N$ only transport, replay, source, and name the displayed rows. Hence the cluster witness has no remaining route through arbitrary subsequence choice or host $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass subsequence nonescape]
\label{thm:bolzano-weierstrass-subsequence-nonescape}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ carrier. The subsequence route exported by $R$ and $Q$ remains inside the retained dyadic mesh supplied by $K$ until the $\RealUp$ cluster seal $E$ is consumed. Consequently the resulting subsequence route exports no open-cover compactness, quotient stream equality, arbitrary choice of subsequence, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-dyadic-mesh-subsequence-witness}. It attaches every selected subsequence index to a retained dyadic cell and a displayed finite sequence-window row.

Apply \autoref{thm:bolzano-weierstrass-cluster-cauchy-window}. The retained cells form the Cauchy window consumed by $Q$, so the subsequence route is fixed by the finite mesh and the monotone-cofinal ledger.

Finally apply \autoref{thm:bolzano-weierstrass-cluster-seal-extraction}. The seal $E$ is reached only after $S,K,R,Q,H,C,P,N$ have displayed that route, leaving no export channel for open-cover compactness, quotient stream equality, arbitrary subsequence choice, or ambient $\RealUp$ completeness.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded-subsequence Cauchy extraction]
\label{thm:bolzano-weierstrass-bounded-subsequence-cauchy-extraction}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet whose bounded-source row, finite interval-tree row, retained-cell monotonicity row, cofinal-window extraction row, and dyadic-mesh subsequence row are displayed. Then $B$ exports a $\RegSeqRatUp$-facing Cauchy subsequence route through $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and $\RealUp$. The route is read only through $S,K,R,Q,E,H,C,P,N$ and supplies no selected subsequence choice, no host compactness principle, no quotient stream equality, and no ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the bounded-source factorization and the finite interval-tree induction. They expose the bounded $\RealUp$ sequence surface $S$ and the finite dyadic refinement tree $K$ before any subsequence row or cluster seal is consumed.

Apply retained-cell monotonicity. Later retained cells refine earlier retained cells through the same closed-bounded interval-net and interval-modulus rows, so the dyadic mesh produces a nested finite ledger rather than an external compactness argument.

Apply cofinal-window extraction and the dyadic-mesh subsequence witness. The row $R$ records a monotone-cofinal $\StreamNameUp$ reindexing ledger built from retained nonempty windows, and $Q$ reads exactly those windows as the $\RegSeqRatUp$ schedule with $\DyadicRatCoreUp$ tolerances.

Finally use subsequence nonescape and the Real cluster seal. The terminal row $E$ is reached only after the bounded source, retained cells, cofinal windows, and regular rational readback have been displayed, so the resulting Cauchy subsequence route remains inside $S,K,R,Q,E,H,C,P,N$ and exports none of the excluded host or choice principles.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass interval-depth witness]
\label{thm:bolzano-weierstrass-interval-depth-witness}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet. For each displayed unary depth whose bounded source window is visible in $S$, the finite interval-tree row $K$ supplies a retained closed-bounded cell, its dyadic mesh ledger, and a nonempty inspected subsequence-window witness before $R$ appends a cofinal index. The witness is read through $\BHist$, $\Cont$, $\hsame$, and $\NameCert$ rows and is not obtained from sequential compactness or any choice-like data.
\end{theorem}
\begin{proof}
Induct on the finite interval tree displayed by $K$. The root case reads the bounded source window from $S$ and the root closed interval from the interval-net carrier.

For the successor step, replay the finite split through $C$ and transport the retained parent row through $H$. One displayed child carries the nonempty inspected window recorded by the packet, and that child supplies the next retained cell.

Only after this finite witness is displayed may $R$ record the next monotone-cofinal subsequence entry. The argument never appeals to sequential compactness without the shown interval cell, window, transport, replay, provenance, and local name.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass tail-cell stability]
\label{thm:bolzano-weierstrass-tail-cell-stability}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet and restrict the extracted route to a later displayed tail of the monotone-cofinal schedule in $R$. The retained cells supplied by $K$ remain nested under the same $\ClosedBoundedIntervalNetUp$ row, the restricted windows remain the windows read by $Q$, and componentwise $\hsame$ transport plus $\Cont$ replay preserves the same $\NameCert$ provenance. Thus subsequence restriction changes only the visible tail ledger, not the cluster package.
\end{theorem}
\begin{proof}
Start from the interval-depth witness. Every selected index in $R$ is attached to a retained cell and a nonempty bounded window, so deleting an initial finite prefix leaves later entries attached to later retained cells.

Use retained-cell monotonicity to compare the tail cells with the original tree. Later cells refine earlier cells through the same interval-net and interval-modulus rows, and $H$ transports this refinement without changing the carrier surface.

Replay the restricted route through $C$ and then read $Q$. The regular rational readback still consumes the retained tail windows; no new sequential compactness theorem, quotient stream, selected subsequence choice, or ambient completeness row is introduced.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass choice-free cluster package]
\label{thm:bolzano-weierstrass-choice-free-cluster-package}
Every accepted $\BolzanoWeierstrassUp$ packet whose interval-depth witness and tail-cell stability rows are displayed packages a regular Cauchy subsequence for $\RegSeqRatUp$ through the finite route $S,K,R,Q,H,C,P,N$. The terminal cluster row $E$ may be read only after that regular package is displayed, and the package contains no arbitrary subsequence selector, no sequential compactness principle without BEDC rows, no quotient real equality, and no ambient $\RealUp$ completeness field.
\end{theorem}
\begin{proof}
First build the finite retained-cell ledger from \autoref{thm:bolzano-weierstrass-interval-depth-witness}. It supplies each depth witness as a displayed interval cell, dyadic mesh row, and nonempty bounded window.

Next apply \autoref{thm:bolzano-weierstrass-tail-cell-stability}. Tail restriction preserves the same nested retained cells and keeps the selected windows inside the same transported and replayed $\NameCert$ surface.

Finally read $Q$ as the $\RegSeqRatUp$ package and then read $E$ as the downstream Real seal. Since all data pass through $S,K,R,Q,H,C,P,N$, the cluster route is choice-free in the BEDC sense: every subsequence and tail fact is carried by finite interval-tree evidence rather than by an external compactness or choice principle.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass finite cluster-retention ledger]
\label{thm:bolzano-weierstrass-finite-cluster-retention-ledger}
Every accepted $\BolzanoWeierstrassUp$ packet $B=(S,K,R,Q,E,H,C,P,N)$ whose bounded-source row, finite interval-tree row, retained-cell row, cofinal-window row, dyadic-mesh row, Cauchy-window row, and cluster-seal row are displayed has a finite cluster-retention ledger over $S,K,R,Q,E,H,C,P,N$. The ledger records exactly the retained dyadic cells, their nonempty bounded sequence windows, the monotone-cofinal subsequence indices, the $\RegSeqRatUp$ Cauchy readback, and the terminal $\RealUp$ cluster seal. It exports no arbitrary subsequence choice, no selected least cluster, no open-cover compactness, no quotient stream equality, and no ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with retained-cell monotonicity. It binds later retained cells to earlier retained cells through the same finite interval-tree rows in $K$, so the retention data is a finite ledger over the displayed interval net rather than a host compactness choice.

Apply cofinal-window extraction and the dyadic-mesh subsequence witness. The row $R$ appends only indices attached to retained nonempty windows from $S$, while the dyadic mesh witness records the finite cell supporting each appended index.

Next apply the cluster Cauchy window theorem. The retained cells and their dyadic diameters determine the $\RegSeqRatUp$ readback row $Q$, and the readback is therefore downstream of the same finite retention ledger.

Finally apply cluster seal extraction. The terminal row $E$ is reached only through the displayed route $S,K,R,Q,H,C,P,N$, so no arbitrary subsequence choice, selected least cluster, open-cover compactness, quotient stream equality, or ambient $\RealUp$ completeness can be exported from the packet.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass source-net exhaustion]
\label{thm:bolzano-weierstrass-source-net-exhaustion}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet. The bounded source row $S$ and interval-net row $K$ exhaust the root source surface for the cluster route: every inspected window, retained dyadic cell, mesh comparison, and bounded interval enclosure consumed by $R,Q,E$ is read first through $S,K,H,C,P,N$ as finite $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ data. No cluster-facing consumer can reach $R,Q$, or $E$ from a source row outside $S$ or an interval-net row outside $K$.
\end{theorem}
\begin{proof}
Start with the root interval-tree obligation of \autoref{thm:bolzano-weierstrass-root-interval-tree-obligation}. It places the bounded source windows and dyadic retained cells inside the displayed finite route before any subsequence or Real seal is read.

Next apply bounded-source factorization and the interval-net obligation. The source row $S$ is the only bounded sequence surface admitted by the carrier, and $K$ is the only closed-bounded interval-net row that can supply retained windows to later rows.

Finally read the finite cluster-retention ledger. Since the ledger records every retained cell, nonempty source window, mesh comparison, and downstream handoff over $S,K,R,Q,E,H,C,P,N$, the root source and interval-net surface is exhausted by $S$ and $K$ together with the structural rows.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass RegSeqRat cluster package]
\label{thm:bolzano-weierstrass-regseqrat-cluster-package}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet whose source-net exhaustion row is displayed. The extraction row $R$, the $\RegSeqRatUp$ readback row $Q$, and the terminal $\RealUp$ seal $E$ form a single cluster package over $S,K,H,C,P,N$: the cofinal subsequence schedule is read from retained finite windows, the regular rational row reads exactly those windows through $\StreamNameUp$ and $\DyadicRatCoreUp$, and the Real seal is reachable only after that regular package has been displayed.
\end{theorem}
\begin{proof}
Use \autoref{thm:bolzano-weierstrass-source-net-exhaustion} to expose the source windows and interval-net cells available to the extraction route. This fixes the only finite data from which $R$ may append cofinal subsequence indices.

Apply the regular subsequence route and the regular subsequence window readback theorem. They identify $R$ as the monotone-cofinal schedule over retained windows and $Q$ as the $\RegSeqRatUp$ readback of those same windows through $\StreamNameUp$ and $\DyadicRatCoreUp$.

Now use cluster seal extraction. The seal row $E$ is downstream of $Q$, and the structural rows $H,C,P,N$ only transport, replay, record provenance, and name the same route. Hence $R,Q,E$ form one displayed RegSeqRat-to-Real cluster package rather than three detachable obligations.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass root obligation package]
\label{thm:bolzano-weierstrass-root-obligation-package}
Every accepted $\BolzanoWeierstrassUp$ packet $B=(S,K,R,Q,E,H,C,P,N)$ whose root interval-tree, root subsequence, Real-seal, bounded-source, and regular-subsequence routes are displayed carries the full root obligation package
$$
S,K,R,Q,E,H,C,P,N .
$$
This package binds the bounded source row, interval-net row, extraction row, RegSeqRat readback row, Real seal row, componentwise $\hsame$ transport, displayed $\Cont$ replay, provenance, and local $\NameCert$ as the exact obligation surface for downstream compactness and Real subsequence consumers. It exports no selected least cluster, arbitrary subsequence choice, open-cover compactness, quotient stream equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
First combine source-net exhaustion with the root interval-tree obligation. The bounded source and interval-net rows $S,K$ expose all finite windows, retained cells, and dyadic mesh data needed by the cluster route.

Next combine the root subsequence extraction obligation with the RegSeqRat cluster package. The extraction row $R$ and readback row $Q$ are forced to consume the retained finite windows already displayed by $S$ and $K$, so no detached subsequence selector or quotient stream can enter.

Finally apply the Real cluster seal and finite cluster-retention ledger. The terminal row $E$ is reached only after the displayed regular package, while $H,C,P,N$ preserve and name the same packet. Therefore the root obligation package is exactly $S,K,R,Q,E,H,C,P,N$ with the stated refusals.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass bounded-sequence admission]
\label{thm:bolzano-weierstrass-bounded-sequence-admission}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet carrying the root obligation package of \autoref{thm:bolzano-weierstrass-root-obligation-package}. The bounded source row $S$ is admitted only as the source surface for the same interval-net row $K$, regular-subsequence row $R$, $\RegSeqRatUp$ readback row $Q$, and $\RealUp$ cluster seal $E$. In particular, the bounded source is read through $S,K,H,C,P,N$ before the rows $R,Q,E$ are exposed, and it cannot be replaced by a detached host sequence, an arbitrary subsequence selector, or an ambient completeness assumption.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-namecert-obligations}. It identifies $S$ as the bounded sequence admission row and places it inside the carrier together with $K,R,Q,E,H,C,P,N$.

Apply \autoref{thm:bolzano-weierstrass-finite-subsequence-obligations} and \autoref{thm:bolzano-weierstrass-interval-net-obligation}. These force the interval-net row $K$ and the regular-subsequence row $R$ to consume the same bounded source windows rather than a second sequence source.

Finally use \autoref{thm:bolzano-weierstrass-root-obligation-package}. The structural rows $H,C,P,N$ bind the bounded source to the later readback and Real seal, so no detached host sequence or completeness principle is exported.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass regular cluster seal]
\label{thm:bolzano-weierstrass-regular-cluster-seal}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet whose bounded-sequence admission row and root obligation package are displayed. The cluster seal $E$ is regular only through the route
$$
S,K,R,Q,E,H,C,P,N .
$$
The row $R$ reads retained finite windows from $S$ through $K$, the row $Q$ reads the same windows as $\RegSeqRatUp$ data, and the row $E$ seals only that regular readback as $\RealUp$ data. No cluster seal is available from a second bounded source, a detached interval net, quotient stream equality, selected subsequence choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with bounded-sequence admission. It fixes the source row $S$ as the only bounded real-sequence surface available to the cluster route.

Use \autoref{thm:bolzano-weierstrass-regseqrat-handoff}. The handoff places the retained windows behind $K$ and $R$ before $Q$ reads them as regular rational data.

Use the interval-net obligation and the root obligation package. Together they bind $K,R,Q$ to the same support rows $H,C,P,N$.

Finally read the Real seal $E$. Since $E$ is downstream of $Q$ in the displayed route, the seal is regular by the carried readback rows and not by a host completeness or selection principle.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass closed-interval cluster export]
\label{thm:bolzano-weierstrass-closed-interval-cluster-export}
An accepted $\BolzanoWeierstrassUp$ packet exports a closed-interval cluster candidate only through the bounded-sequence admission row $S$, the closed interval net row $K$, the regular subsequence extraction row $R$, the $\RegSeqRatUp$ readback row $Q$, and the terminal $\RealUp$ seal $E$, with $H,C,P,N$ transporting, replaying, sourcing, and naming the same route. The export refuses arbitrary subsequence choice, open-cover compactness, quotient stream equality, selected least cluster points, and ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with bounded-source factorization and bounded-sequence admission. These rows fix $S$ as the only source of sequence data and force every cluster-facing read to pass through the displayed bounded source.

Next apply finite interval-tree induction and retained-cell monotonicity. The closed interval net row $K$ supplies the retained cells and their finite refinement route, so the packet cannot switch to an open-cover compactness proof or a detached interval net.

Use cofinal-window extraction and the regular cluster seal. The extraction row $R$ reads retained windows through $K$, the readback row $Q$ records the corresponding $\RegSeqRatUp$ data, and the seal row $E$ exports only that regular readback as $\RealUp$ cluster evidence.

Finally apply cluster-seal nonescape. The structural rows $H,C,P,N$ preserve and name the same packet, and no carrier row remains from which arbitrary subsequence choice, quotient equality, least-cluster selection, or ambient completeness could be projected.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass cluster-seal nonescape]
\label{thm:bolzano-weierstrass-cluster-seal-nonescape}
For every accepted $\BolzanoWeierstrassUp$ packet $B=(S,K,R,Q,E,H,C,P,N)$ carrying the bounded-sequence admission and regular cluster-seal rows, any cluster-facing consumer remains inside the displayed surface
$$
S,K,R,Q,E,H,C,P,N .
$$
The consumer may read a bounded source window, a retained interval-net cell, a regular-subsequence ledger, a $\RegSeqRatUp$ readback row, and the terminal $\RealUp$ seal, but it cannot escape to an unlisted source row, an unlisted interval net, a selected least cluster point, quotient real equality, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:bolzano-weierstrass-bounded-sequence-admission}. It fixes $S$ and $K$ as the source and interval-net surface for the cluster route.

Apply \autoref{thm:bolzano-weierstrass-regular-cluster-seal}. It fixes $R,Q,E$ as the regular-subsequence, regular readback, and Real-seal surface downstream of those rows.

The support rows $H,C,P,N$ are the only transport, replay, provenance, and local naming coordinates in the carrier of \autoref{def:bolzano-weierstrass-carrier}. Therefore every cluster-facing read remains inside $S,K,R,Q,E,H,C,P,N$, and the refused host-level objects have no row from which they can be projected.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass retained-window refinement]
\label{thm:bolzano-weierstrass-window-retention-refinement}
Let $B=(S,K,R,Q,E,H,C,P,N)$ be an accepted $\BolzanoWeierstrassUp$ packet carrying the root obligation package of \autoref{thm:bolzano-weierstrass-root-obligation-package}. Every retained dyadic interval cell used by the cluster route is read through
$$
S,K,R,Q,H,C,P,N
$$
before the terminal $\RealUp$ cluster seal $E$ is exposed. The refinement preserves the same $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, and $\RealUp$ route: no retained window may be reclassified through a new stream name, a detached dyadic grid, a second rational-readback package, or a host compactness selector.
\end{theorem}
\begin{proof}
Start with the root interval-tree obligation. It displays the retained dyadic cells through $S$ and $K$, so each retained window is already attached to the bounded source and interval-net rows before the extraction route is read.

Next apply the root subsequence extraction obligation. The row $R$ consumes only those retained cells, and the $\StreamNameUp$ and $\DyadicRatCoreUp$ data used by the extraction remain the ones displayed by the same source and interval-net package.

Now use the RegSeqRat cluster package. The readback row $Q$ is the $\RegSeqRatUp$ route for the retained windows already carried by $S,K,R$, so it cannot introduce a second rational-readback surface or a detached dyadic grid.

Finally apply the root Real-seal obligation and the root obligation package. The cluster seal $E$ is downstream of $S,K,R,Q,H,C,P,N$, while $H,C,P,N$ transport, replay, record provenance, and name the same route. Hence the retained-window induction is preserved all the way to the $\RealUp$ seal without importing a new stream, grid, readback package, or host selector.
\end{proof}

\input{parts/concrete_instances/bolzanoweierstrass/public_subsequence_selector}

\falsifiablePrediction{Every $\BolzanoWeierstrassUp$ cluster read factors through the displayed interval net and regular Cauchy subsequence rows before reaching the $\RealUp$ seal.}

\independenceWitness{closedboundedintervalnet, closedboundedintervaluniformmodulus, regularcauchysubsequence, regseqrat, real: $\BolzanoWeierstrassUp$ is not bijective to any listed sibling because it jointly carries a bounded sequence surface, finite interval nets, monotone-cofinal subsequence extraction, regular rational readback, RealUp cluster sealing, transport, continuation, package provenance, and local naming.}

\closureat{BolzanoWeierstrassUp}{seedStr}
\closureat{BolzanoWeierstrassUp}{obligationStr}

\begin{closurestatus}{\BolzanoWeierstrassUp}
  \constructivestory{A $\BolzanoWeierstrassUp$ packet is generated from a bounded RealUp sequence surface, finite closed bounded interval nets, interval-modulus compatibility, a monotone-cofinal regular Cauchy subsequence extraction row, RegSeqRat readback, a RealUp cluster seal, componentwise hsame transport, displayed Cont replay, Pkg provenance, and a local NameCert row.}
  \theoryclosure{\scopedClosure}
  \scopeclosed{\autoref{def:bolzano-weierstrass-carrier}, \autoref{thm:bolzano-weierstrass-namecert-obligations}, \autoref{thm:bolzano-weierstrass-regular-subsequence-route}, \autoref{thm:bolzano-weierstrass-bounded-source-factorization}, \autoref{thm:bolzano-weierstrass-finite-interval-tree-induction}, \autoref{thm:bolzano-weierstrass-retained-cell-monotonicity}, \autoref{thm:bolzano-weierstrass-cofinal-window-extraction}, \autoref{thm:bolzano-weierstrass-real-cluster-seal}, and \autoref{thm:bolzano-weierstrass-cluster-seal-extraction} bind the bounded-sequence subsequence compactness route through the carrier, NameCert obligations, bounded sequence extraction, finite interval nets, regular-subsequence route, RegSeqRat readback, and Real seal rows.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, open-cover compactness, host completeness, quotient equality of streams, least cluster selection, or arbitrary subsequence choice.}
  \upgradepath{Lean closure requires carrier admission, NameCert obligations, regular-subsequence route, Real cluster seal, and TasteGate field faithfulness for BEDC.Derived.BolzanoWeierstrassUp.}
\end{closurestatus}
