\chapter{A Concrete Naming Certificate for $\AlgClosureUp$}
\label{ch:concrete-instances-algclosure-namecert}

The algebraic-closure interface $\AlgClosureUp$ packages a field extension in which every nonconstant polynomial over the base field has a root. It depends on $\NameCert_{\FieldExtUp}$ (\autoref{ch:concrete-instances-fieldext-namecert}) and $\NameCert_{\PolynomialUp}$ (\autoref{ch:concrete-instances-polynomial-namecert}).

\section{Carrier definition}
\label{sec:algclosure-carrier}

An $\AlgClosureUp$ carrier packet is a finite $\mathsf{BHist}$ row family over
the consumed $\NameCert_{\FieldExtUp}$ and $\NameCert_{\PolynomialUp}$ sources.
It contains a field-extension row $F$, a nonconstant polynomial request row $p$,
a displayed root endpoint $r$, a classifier transport row $H$, a finite root
ledger $L$, and a package provenance row $\Pi:\Pkg$.

\begin{theorem}[AlgClosureUp carrier source obligation]
\label{thm:algclosure-carrier-source-obligation}
Every accepted $\AlgClosureUp$ carrier packet is sourced by a
$\FieldExtUp$ extension row, a $\PolynomialUp$ nonconstant-polynomial request
row over that extension, the displayed root endpoint row, the $\hsame$
classifier transport row, the shared $\Pkg$ provenance row, and the finite
root-ledger rows. Conversely, these rows repack as the carrier surface of the
same $\AlgClosureUp$ packet.
\end{theorem}
\leanchecked{BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_source\_obligation}
\begin{proof}
Unpack the carrier packet into its displayed $\mathsf{BHist}$ coordinates. The
$\FieldExtUp$ row supplies the base and extension histories, and the
$\PolynomialUp$ row supplies the finite coefficient and nonconstant-request
histories over that same extension row.

The root endpoint is not read from a host algebraic closure. It is a carried
history endpoint whose acceptance is recorded by the finite ledger $L$, whose
transport is the displayed $\hsame$ row $H$, and whose provenance is the single
package row $\Pi$.

For the converse, take precisely those six row families and place them back
into the packet slots. The carrier predicate asks for no further data, so the
same rows reconstruct the accepted carrier surface.
\end{proof}

\begin{theorem}[AlgClosureUp polynomial-root classifier obligation]
\label{thm:algclosure-polynomial-root-classifier-obligation}
Two accepted $\AlgClosureUp$ root-witness packets classify together exactly
when their $\FieldExtUp$ source rows classify together, their $\PolynomialUp$
nonconstant request rows classify over the transported field-extension source,
their displayed root endpoints are related by the packet $\hsame$ row, and
their finite root ledgers and $\Pkg$ provenance rows are the corresponding
transported rows.
\end{theorem}
\leanchecked{BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_polynomial\_root\_classifier\_obligation}
\begin{proof}
Read the two packets through
\autoref{thm:algclosure-carrier-source-obligation}. Each packet exposes the
same six kinds of rows: field-extension source, polynomial request, root
endpoint, classifier transport, root ledger, and provenance.

Compare the field-extension projections first. The $\FieldExtUp$ classifier
binds the base and extension histories, so the polynomial request in the second
packet is read over the transported extension source rather than over a fresh
ambient field.

Now compare the polynomial and root projections. The $\PolynomialUp$ classifier
transports the nonconstant request row, the displayed $\hsame$ row transports
the root endpoint, and the ledger/provenance clauses say that $L$ and $\Pi$ are
carried along the same comparison. These are all classifier fields, hence the
packets classify together exactly under this componentwise finite comparison.
\end{proof}

\begin{theorem}[AlgClosureUp ledger readback obligation]
\label{thm:algclosure-ledger-readback-obligation}
The visible root-certificate ledger of an accepted $\AlgClosureUp$ packet is
exactly the finite family consisting of the $\FieldExtUp$ source row, the
$\PolynomialUp$ nonconstant-polynomial request row, the displayed root endpoint
row, the root-satisfaction row, the $\hsame$ classifier transport row, and the
$\Pkg$ provenance row. No other root certificate row is visible downstream.
\end{theorem}
\begin{proof}
Begin with the carrier source obligation. It identifies the only source and
endpoint rows in the packet, namely $F$, $p$, $r$, $H$, $L$, and $\Pi$.

Project the finite root ledger $L$. Its readback rows are exactly the
polynomial request, the displayed endpoint, and the carried satisfaction
history witnessing that the request has the endpoint as a root. The same ledger
also records the $\hsame$ transport used by the classifier obligation.

Since the packet has only one provenance coordinate, every visible ledger row
returns to $\Pi:\Pkg$. Thus downstream readback is exhausted by the listed
finite family.
\end{proof}
\leanchecked{BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_ledger\_readback\_obligation}

\begin{theorem}[AlgClosureUp root-witness transport coverage]
\label{thm:algclosure-root-witness-transport-coverage}
If two accepted $\AlgClosureUp$ root-witness packets classify together, then
every visible root-satisfaction row in the first packet transports to a
visible root-satisfaction row in the second packet over the transported
$\FieldExtUp$ and $\PolynomialUp$ sources. The transported row keeps the same
$\Pkg$ provenance, and it introduces no ambient algebraic-closure object and
no quotient root.
\end{theorem}
\leanchecked{BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_root\_witness\_transport\_coverage}
\begin{proof}
First unpack both root-witness packets through
\autoref{thm:algclosure-carrier-source-obligation}. Each side exposes only the
field-extension source row, the nonconstant polynomial request, the displayed
root endpoint, the classifier transport row, the finite ledger, and the
package provenance.

Next apply
\autoref{thm:algclosure-polynomial-root-classifier-obligation}. The packet
classifier transports the $\FieldExtUp$ source first, then reads the
$\PolynomialUp$ request over that transported source, and then carries the
endpoint, ledger, and provenance rows along the same comparison.

Finally re-read the target packet ledger with
\autoref{thm:algclosure-ledger-readback-obligation}. The root-satisfaction row
is one of the visible ledger rows, so the transported endpoint and polynomial
request determine the corresponding visible satisfaction row in the second
packet. Because the readback ledger contains only finite BEDC rows and the
single $\Pkg$ coordinate, no ambient algebraic closure or quotient root is
exported.
\end{proof}

\begin{theorem}[AlgClosureUp standard boundary obligation]
\label{thm:algclosure-standard-boundary-obligation}
The $\AlgClosureUp$ carrier packet contains no host algebraic-closure object,
no quotient root object, and no uncarried root set. Its boundary is exactly the
finite $\mathsf{BHist}$, $\Cont$, $\hsame$, $\NameCert_{\FieldExtUp}$,
$\NameCert_{\PolynomialUp}$, and $\Pkg$ surface displayed by the accepted
packet.
\end{theorem}
\begin{proof}
Use \autoref{thm:algclosure-ledger-readback-obligation} to list the visible
root-certificate rows. Each row is a carried history, a continuation ledger
entry, an $\hsame$ transport, a consumed naming certificate, or a package
provenance row.

A host algebraic closure would require an additional carrier object with
global roots for all polynomials. A quotient root object would require an
additional quotient equality or orbit representative. Neither field is present
in the accepted packet, and neither is part of the readback ledger.

Therefore the boundary is the displayed BEDC surface alone. The chapter records
root existence only as finite carried certificates for the requested
nonconstant polynomial rows.
\end{proof}

\begin{theorem}[AlgClosureUp downstream consumer obligation]
\label{thm:algclosure-downstream-consumer-obligation}
Every downstream consumer of an accepted $\AlgClosureUp$ packet may read only
the finite $\FieldExtUp$ source rows, $\PolynomialUp$ nonconstant-polynomial
request rows, displayed root rows, classifier transport rows, finite root
ledger rows, and $\Pkg$ provenance rows. A consumer receives no ambient
algebraic closure, root quotient, or unlisted host-algebra datum.
\end{theorem}
\begin{proof}
First apply \autoref{thm:algclosure-carrier-source-obligation}. This fixes the
carrier-facing rows available to the consumer: the field-extension source, the
polynomial request, the root endpoint, transport, ledger, and provenance.

Next apply \autoref{thm:algclosure-polynomial-root-classifier-obligation}. Any
consumer-side comparison must use the same $\FieldExtUp$ and $\PolynomialUp$
source comparisons, the displayed root $\hsame$ row, and the transported ledger
and provenance rows.

Finally apply \autoref{thm:algclosure-standard-boundary-obligation}. It removes
host algebraic closures, quotient roots, and uncarried root sets from the
consumer interface. The downstream surface is therefore exactly the finite
row family listed in the statement.
\end{proof}

\section{The certificate}
\label{sec:algclosure-certificate}

\begin{theorem}[AlgClosureUp root carrier obligation surface]
\label{thm:algclosure-root-carrier-obligation-surface}
An $\AlgClosureUp$ carrier row is exactly a $\FieldExtUp$ source row together
with a $\PolynomialUp$ root-ledger row over the BEDC primitives
$\mathsf{BHist}$, $\hsame$, $\Cont$, and $\Pkg$. The carrier exposes the base
and extension histories, the nonconstant polynomial request, the displayed
root endpoint, the transported classifier row, the finite satisfaction ledger,
and the package provenance, and it exposes no ambient algebraic-closure
carrier outside those rows.
\end{theorem}
\begin{proof}
Unpack the seed carrier packet. Its first projection is the consumed
$\FieldExtUp$ source, so the base-field and extension histories are already
fixed as displayed $\mathsf{BHist}$ rows with their classifier transport.

Project the polynomial side next. The consumed $\PolynomialUp$ request supplies
the finite coefficient ledger and the nonconstant-row witness over the same
field-extension source, while the root endpoint and satisfaction row are
carried as finite histories connected by the displayed $\hsame$ and $\Cont$
data.

Repack these projections with the single $\Pkg$ provenance row. The packet has
no constructor for a host algebraic closure or unlisted root carrier, so the
listed $\FieldExtUp$ and $\PolynomialUp$ rows are the whole carrier obligation
surface.
\end{proof}

\begin{theorem}[AlgClosureUp polynomial root ledger obligation]
\label{thm:algclosure-polynomial-root-ledger-obligation}
Every admitted polynomial-root row in an $\AlgClosureUp$ packet projects to
the displayed $\PolynomialUp$ coefficient ledger, the inherited $\FieldUp$
operation rows carried by the $\FieldExtUp$ source, and the $\hsame$ transport
that relates the displayed root endpoint to the polynomial satisfaction row.
The projection preserves the same finite $\mathsf{BHist}$ ledger and the same
$\Pkg$ provenance.
\end{theorem}
\begin{proof}
Start from the admitted root row and read it through
\autoref{thm:algclosure-carrier-source-obligation}. This gives the
$\FieldExtUp$ source, the $\PolynomialUp$ request, the endpoint, transport,
ledger, and provenance coordinates.

The $\PolynomialUp$ projection is the coefficient ledger for the requested
nonconstant polynomial. Since that request is over the displayed field
extension, its scalar operations are exactly the inherited $\FieldUp$ rows
available through the $\FieldExtUp$ source rather than operations from a host
field object.

Finally project the root endpoint and satisfaction row from the finite ledger.
The $\hsame$ coordinate transports the endpoint along the classifier
comparison, and the ledger repacks with the same $\mathsf{BHist}$ rows and
$\Pkg$ provenance. No quotient root or choice-selected representative is read
by this projection.
\end{proof}

\begin{theorem}[AlgClosureUp FieldExt consumer boundary]
\label{thm:algclosure-fieldext-consumer-boundary}
Downstream $\FieldExtUp$ and $\PolynomialUp$ consumers of an accepted
$\AlgClosureUp$ packet read only the displayed field-extension rows,
polynomial coefficient ledgers, root endpoint rows, satisfaction ledgers,
$\hsame$ transports, finite $\Cont$ readbacks, and $\Pkg$ provenance. They do
not receive a quotient field, a classical algebraic closure, or a
choice-picked root outside the displayed BEDC rows.
\end{theorem}
\begin{proof}
First apply \autoref{thm:algclosure-root-carrier-obligation-surface}. This
confines every consumer-facing carrier read to the consumed $\FieldExtUp$
source, the polynomial request, the displayed endpoint, transport, ledger, and
provenance rows.

Next apply \autoref{thm:algclosure-polynomial-root-ledger-obligation}. It
identifies the coefficient ledger, inherited $\FieldUp$ operations, root
satisfaction row, and $\hsame$ transport available to polynomial consumers.

The remaining consumer read is a boundary question. Use
\autoref{thm:algclosure-downstream-consumer-obligation} to repack the
projected rows as the exported surface. Since each projection came from the
finite packet coordinates, no quotient field, classical algebraic closure, or
choice-picked root is present.
\end{proof}

\closureat{AlgClosureUp}{seedStr}[BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_source\_obligation]
\closureat{AlgClosureUp}{scopedStr}[BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_polynomial\_root\_classifier\_obligation]
\closureat{AlgClosureUp}{scopedStr}[BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_root\_witness\_transport\_coverage]

\begin{closurestatus}{\AlgClosureUp}
  \theoryclosure{\scopedClosure}
  \scopeclosed{The obligation surface binds the carrier, polynomial-root classifier, finite root ledger readback, transport coverage, standard boundary, and downstream consumer rows over $\FieldExtUp$, $\PolynomialUp$, $\mathsf{BHist}$, $\Cont$, $\hsame$, and $\Pkg$.}
  \formalstatus{\auditCleanV}
  \leantarget{BEDC.Derived.AlgClosureUp.AlgClosureCarrierPacket\_root\_witness\_transport\_coverage}
  \bridgestatus{none}
  \notclaimed{This chapter does not close ambient algebraic closures, quotient roots, host algebraic-closure objects, or unlisted root carriers.}
  \upgradepath{Public closure requires a single exported $\AlgClosureUp$ public certificate surface over the scoped carrier, classifier, root ledger, transport, standard boundary, and consumer rows.}
\end{closurestatus}
