\chapter{A Concrete Naming Certificate for $\MonotoneSubsequenceUp$}
\label{ch:concrete-instances-monotone-subsequence-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\MonotoneSubsequenceUp$ packet records monotone subsequences as displayed finite unary selector rows. It does not select an infinite subsequence by countable choice. The packet sits between the regular-Cauchy subsequence surface of \autoref{ch:concrete-instances-regular-cauchy-subsequence-namecert}, the cofinal index witness of \autoref{ch:concrete-instances-cofinalsubsequence-namecert}, and the monotone-Cauchy route of \autoref{ch:concrete-instances-monotonecauchy-namecert}. Its endpoint side is read through the $\StreamNameUp$ windows of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, and the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}.

\begin{definition}[Monotone subsequence carrier]
\label{def:monotone-subsequence-carrier}
A $\MonotoneSubsequenceUp$ carrier is a finite $\BHist$ packet
$$
U=(S,M,Q,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the source $\RegularCauchySubsequenceUp$ row whose inspected finite windows are being selected.
\item $M$ is the finite monotone unary selector ledger; each displayed entry records a selector value, its source index, and the comparison row certifying monotonicity against the previously displayed selector entries.
\item $Q$ is the $\CofinalSubsequenceUp$ evidence row for the inspected thresholds, limited to the thresholds actually present in the packet.
\item $W$ is the finite family of selected $\StreamNameUp$ windows read from $S$ through the ledger $M$ and the cofinal evidence $Q$.
\item $D$ is the $\DyadicRatCoreUp$ observation ledger extracted from the selected windows.
\item $R$ is the $\RegSeqRatUp$ handoff row reached from $W$ and $D$.
\item $E$ is the $\RealUp$ seal row exposed only after the selected regular-rational handoff has been displayed.
\item $H$ stores componentwise $\hsame$ transport for the source row, monotone selector ledger, cofinality evidence, selected windows, dyadic observations, regular handoff, Real seal, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from $S,M,Q$ to $W$, from $W$ to $D$, from $D$ to $R$, and from $R$ to $E$.
\item $P$ is the $\Pkg$ provenance over $\MonotoneSubsequenceUp$, $\RegularCauchySubsequenceUp$, $\CofinalSubsequenceUp$, $\MonotoneCauchyUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\MonotoneSubsequenceUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these eleven rows. It has no coordinate for a host subsequence equality test, a countable-choice selector, a quotient stream, an ambient completeness principle, or a hidden infinite monotone-subsequence object.
\end{definition}
\leanchecked{BEDC.Derived.MonotoneSubsequenceUp.TasteGate.MonotoneSubsequenceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Monotone subsequence NameCert obligations]
\label{thm:monotone-subsequence-namecert-obligations}
For every accepted $\MonotoneSubsequenceUp$ carrier $U=(S,M,Q,W,D,R,E,H,C,P,N)$, the local $\NameCert_{\MonotoneSubsequenceUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the displayed eleven-row packet;
\item monotone selector stability for the finite unary selector ledger $M$ under the recorded $\hsame$ transports;
\item cofinal coverage for every inspected threshold listed in $Q$;
\item selected-window $\RegSeqRatUp$ handoff through $W,D,R$ before the terminal $\RealUp$ seal row $E$ is consumed;
\item non-escape from host subsequence equality, countable choice, quotient-stream equality, and ambient completeness.
\end{enumerate}
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:monotone-subsequence-carrier}. The source row $S$, selector ledger $M$, cofinality evidence $Q$, selected windows $W$, dyadic observations $D$, handoff $R$, seal $E$, and structural rows $H,C,P,N$ are the only coordinates available to the classifier.

The monotone and cofinal faces are finite. Selector stability reads the displayed comparisons inside $M$, while cofinal coverage reads only the inspected thresholds recorded in $Q$. No step quantifies over an unbounded family of undisplayed requests.

The analytic endpoint is downstream from the same finite route. The selected $\StreamNameUp$ windows $W$ produce the dyadic ledger $D$, the dyadic ledger produces the $\RegSeqRatUp$ handoff $R$, and the Real seal $E$ is available only after that handoff.

Finally inspect the excluded objects. Host subsequence equality, countable choice, quotient streams, and ambient completeness are not rows of $U$, and the structural rows only transport, replay, source, and name the displayed packet. The five listed obligations therefore exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Monotone subsequence regular-Cauchy handoff]
\label{thm:monotone-subsequence-regular-cauchy-handoff}
Every accepted $\MonotoneSubsequenceUp$ packet hands its selected monotone finite windows to $\RegSeqRatUp$ before any $\RealUp$ seal can be consumed. Equivalently, every seal-facing route factors through
$$
S,M,Q\longmapsto W\longmapsto D\longmapsto R\longmapsto E
$$
together with $H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with the selected-window rows. The continuation route records that $W$ is read from the source regular-Cauchy subsequence row $S$, the monotone selector ledger $M$, and the cofinal threshold evidence $Q$.

Next read the regular-rational handoff. The dyadic observation ledger $D$ is extracted from the selected StreamName windows, and the row $R$ is the displayed $\RegSeqRatUp$ handoff reached from those dyadic observations.

Only then is the seal row available. The row $E$ is part of the packet as the Real-facing endpoint reached through $R$, while $H,C,P,N$ only preserve the same route by transport, replay, provenance, and local naming.

Thus a consumer that tries to use the $\RealUp$ seal without the selected-window $\RegSeqRatUp$ handoff leaves the accepted $\MonotoneSubsequenceUp$ carrier.
\end{proof}

\closureat{MonotoneSubsequenceUp}{seedStr}

\begin{closurestatus}{\MonotoneSubsequenceUp}
  \constructivestory{A $\MonotoneSubsequenceUp$ packet is generated from a source regular-Cauchy subsequence row, a finite monotone unary selector ledger, inspected-threshold cofinality evidence, selected StreamName windows, DyadicRatCore observations, a RegSeqRat handoff, a RealUp seal, componentwise transport, displayed continuation replay, package provenance, and local naming.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:monotone-subsequence-carrier}, \autoref{thm:monotone-subsequence-namecert-obligations}, and \autoref{thm:monotone-subsequence-regular-cauchy-handoff} declare the finite selector carrier, its NameCert obligations, and the regular-Cauchy handoff boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not claim Bolzano-Weierstrass, sequential compactness, choice-selected subsequences, quotient-stream equality, host subsequence equality, Lean verification, bridge checking, or RealUp completeness.}
  \upgradepath{Obligation closure requires checked carrier admission, monotone selector stability, inspected-threshold cofinal coverage, selected-window RegSeqRat handoff, and seal-route non-escape for the same packet.}
\end{closurestatus}
