\chapter{A Concrete Naming Certificate for $\BishopRealComparisonUp$}
\label{ch:concrete-instances-bishoprealcomparison-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\BishopRealComparisonUp$ packet records the finite comparison surface between Bishop-style regular-Cauchy real names, located-real readbacks, and Dedekind-cut boundary rows without importing quotient reals, trichotomy, host real equality, or ambient completeness.

The packet is a human-origin L10 comparison certificate between the regular-Cauchy presentation of \autoref{ch:concrete-instances-bishopreal-namecert}, the completion-facing handoff of \autoref{ch:concrete-instances-real-cauchy-completion-namecert}, the finite located readback of \autoref{ch:concrete-instances-locatedreal-namecert}, and the rounded cut boundary of \autoref{ch:concrete-instances-dedekindcut-namecert}. It uses those sibling surfaces only as displayed certificate rows; it does not identify them as equivalent real constructions.

\begin{definition}[BishopRealComparison carrier]
\label{def:bishop-real-comparison-carrier}
A $\BishopRealComparisonUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
X=(B,C,L,D,R,S,H,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $B$ is the accepted $\BishopRealUp$ row exposing a regular-Cauchy real name, its scheduled finite windows, dyadic tolerance rows, located-apartness evidence, and visible $\RealUp$ seal;
\item $C$ is the $\RealCauchyCompletionUp$ row reached from the same regular-Cauchy source surface, recording the completion-facing handoff without adding a quotient completion point;
\item $L$ is the $\LocatedRealUp$ row that reads the same regular source through finite dyadic location windows;
\item $D$ is the $\DedekindCutUp$ boundary row carrying lower and upper rational observations, roundedness, locatedness, disjointness, and rational embedding data;
\item $R$ is the shared $\RealUp$ seal row through which all real-facing consumers must pass;
\item $S$ is the readback ledger naming the $\StreamNameUp$, $\RegSeqRatUp$, and $\DyadicRatCoreUp$ schedules, regular-rational rows, and tolerance packets used by $B,C,L$, and $D$;
\item $H$ records componentwise $\hsame$ and displayed $\Cont$ transports among the Bishop, completion, located, Dedekind-boundary, seal, and readback rows;
\item $P$ is the $\Pkg$ provenance over $\BishopRealUp$, $\RealCauchyCompletionUp$, $\LocatedRealUp$, $\DedekindCutUp$, $\RealUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$;
\item $N$ is the local $\NameCert_{\BishopRealComparisonUp}$ row.
\end{enumerate}
The carrier classifier compares two accepted packets only by replaying the displayed finite rows $B,C,L,D,R,S,H,P,N$. It has no coordinate for quotient-real equality, trichotomy, host real equality, a selected limit, a completeness theorem, or a proof that Bishop, located, and Dedekind presentations are globally equivalent.
\end{definition}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.TasteGate.BishopRealComparisonTasteGate\_single\_carrier\_alignment}

\begin{theorem}[BishopRealComparison NameCert obligations]
\label{thm:bishop-real-comparison-namecert-obligations}
For every accepted $\BishopRealComparisonUp$ carrier $X=(B,C,L,D,R,S,H,P,N)$, the local $\NameCert_{\BishopRealComparisonUp}$ obligation surface consists exactly of carrier admission for the displayed packet, Bishop-real admission through $B$, completion handoff admission through $C$, located-readback admission through $L$, Dedekind-boundary admission through $D$, shared $\RealUp$ seal admission through $R$, finite StreamName/RegSeqRat/DyadicRatCore readback through $S$, componentwise $\hsame$ and $\Cont$ transport through $H$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_namecert\_obligations}
\begin{proof}
Project the carrier of \autoref{def:bishop-real-comparison-carrier}. The rows $B,C,L,D,R,S,H,P,N$ are the complete displayed coordinates of one finite $\mathsf{BHist}$ packet.

Read the four analytic-facing rows in route order. The Bishop row supplies the regular-Cauchy name surface, the completion row supplies the handoff reached from that surface, the located row supplies finite dyadic location readback, and the Dedekind row supplies lower and upper rational boundary observations.

The shared seal and readback rows then bind the comparison. The $\RealUp$ seal $R$ is reached only after the regular windows, rational readback rows, and dyadic tolerance packets named by $S$ have been exposed.

Finally, $H,P$, and $N$ provide transport, provenance, and local naming for exactly those rows. Since no coordinate stores quotient equality, trichotomy, host equality, a selected limit, or ambient completeness, no further NameCert obligation can be read from the packet.
\end{proof}

\begin{theorem}[BishopRealComparison Cauchy-Dedekind boundary]
\label{thm:bishop-real-comparison-cauchy-dedekind-boundary}
Every completion-facing or cut-facing read exported by an accepted $\BishopRealComparisonUp$ packet factors through the same finite regular-Cauchy source and tolerance surface. The completion row $C$ is read through the Bishop row $B$, the shared readback ledger $S$, and the seal row $R$; the Dedekind boundary row $D$ is read through the rational observation and dyadic tolerance rows already named by $S$.

Thus the packet gives a Cauchy-to-Dedekind boundary comparison surface, not an equivalence theorem between quotient completions and Dedekind cuts.
\end{theorem}
\begin{proof}
First expose the regular-Cauchy source. The Bishop row $B$ carries the scheduled finite windows, regular-rational name, dyadic tolerance data, and visible $\RealUp$ seal that the comparison packet is allowed to inspect.

Next follow the completion route. The row $C$ is a completion-facing handoff attached to the same source surface, so a consumer cannot read $C$ before it has read $B$ and the StreamName/RegSeqRat/DyadicRatCore ledger $S$.

Now follow the cut-facing boundary. The row $D$ supplies lower and upper rational observations, roundedness, locatedness, disjointness, and rational embedding data, but the public comparison reaches those observations only through the rational and dyadic rows named in $S$.

The conclusion is therefore a boundary statement. The carrier displays a finite route from Cauchy-name rows to cut-boundary observations, while the excluded quotient completion, cut equality, and ambient equivalence data remain absent from every coordinate.
\end{proof}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_cauchy\_dedekind\_boundary}

\begin{theorem}[BishopRealComparison located readback]
\label{thm:bishop-real-comparison-located-readback}
For an accepted $\BishopRealComparisonUp$ packet $X=(B,C,L,D,R,S,H,P,N)$, every located-real consumer read factors first through the Bishop regular-Cauchy row $B$, then through the shared finite readback ledger $S$, and only then through the $\LocatedRealUp$ row $L$. The read exposes the same scheduled $\StreamNameUp$ windows, $\RegSeqRatUp$ rational rows, $\DyadicRatCoreUp$ tolerance packets, and $\RealUp$ seal row $R$ that the completion and Dedekind-boundary routes use.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonCarrier\_located\_readback}
\begin{proof}
Project the located coordinate $L$ from the carrier. It is not an independent located real object; it is stored with $B$, $S$, and $R$ in the same finite packet.

Read the shared ledger $S$. It names the finite windows, regular-rational rows, and dyadic tolerance packets through which the Bishop, completion, located, and Dedekind-boundary routes are all replayed.

Transport the located read through $H$. The componentwise $\hsame$ and displayed $\Cont$ routes preserve only the scheduled rows already listed in $S$, so the consumer sees the same source and tolerance surface as the other comparison routes.

The located readback is therefore shared rather than detached. No extra order relation, quotient representative, host equality, or completion point is available to the consumer after $L$ has been read.
\end{proof}

\begin{theorem}[BishopRealComparison non-escape]
\label{thm:bishop-real-comparison-nonescape}
An accepted $\BishopRealComparisonUp$ packet exports only the finite comparison surface
$$
B,C,L,D,R,S,H,P,N.
$$
No downstream consumer can obtain quotient reals, trichotomy, host real equality, a selected limit, ambient completeness, or a global equivalence between Bishop Cauchy names, located reals, and Dedekind cuts from the packet alone.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_nonescape}
\begin{proof}
Read the carrier inventory. The public surface consists exactly of the Bishop row, completion handoff, located readback, Dedekind boundary, shared real seal, shared finite readback ledger, transport row, provenance row, and local naming row.

Apply \autoref{thm:bishop-real-comparison-namecert-obligations} to exhaust the local certificate obligations. Every admitted consumer read is one of the displayed rows or a replay of those rows through $H,P$, and $N$.

Apply \autoref{thm:bishop-real-comparison-cauchy-dedekind-boundary} and \autoref{thm:bishop-real-comparison-located-readback} to the two analytic-facing exits. The completion, located, and Dedekind-boundary consumers all pass through the same finite source/readback surface before reaching their public rows.

The excluded data have no coordinate in the packet and no route through the displayed obligations. Hence a downstream consumer cannot escape to quotient equality, trichotomy, host real equality, selected limits, ambient completeness, or a global presentation-equivalence theorem.
\end{proof}

\begin{theorem}[BishopRealComparison source induction]
\label{thm:bishop-real-comparison-source-induction}
Every accepted $\BishopRealComparisonUp$ packet is obtained by finite induction over the displayed rows
$$
B,C,L,D,R,S,H,P,N.
$$
The induction first admits the Bishop row, then the completion handoff, located row, Dedekind boundary row, shared seal, readback ledger, componentwise transport, provenance, and local naming rows. It refuses quotient equality, trichotomy, selected limits, and ambient completeness at every step.
\end{theorem}
\begin{proof}
The base step is the carrier projection of \autoref{def:bishop-real-comparison-carrier}. It exposes a finite packet whose public coordinates are exactly $B,C,L,D,R,S,H,P,N$.

For the analytic rows, apply \autoref{thm:bishop-real-comparison-namecert-obligations}. The Bishop row $B$ supplies the regular-Cauchy source, $C$ is admitted only as the completion-facing handoff from that source, $L$ is admitted only as the located readback, and $D$ is admitted only as the Dedekind-boundary read.

For the shared rows, use \autoref{thm:bishop-real-comparison-cauchy-dedekind-boundary} and \autoref{thm:bishop-real-comparison-located-readback}. They force the completion, located, and cut-facing exits through the same seal $R$ and readback ledger $S$.

The final induction steps add $H,P$, and $N$ as transport, provenance, and local naming rows for the already displayed surface. By \autoref{thm:bishop-real-comparison-nonescape}, no induction case has a coordinate from which quotient equality, trichotomy, selected limits, or ambient completeness can be introduced.
\end{proof}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_source\_induction}

\begin{theorem}[BishopRealComparison located-cut transport]
\label{thm:bishop-real-comparison-located-cut-transport}
In an accepted $\BishopRealComparisonUp$ packet, a located read and a Dedekind boundary read transported through the same $S,H,P,N$ rows remain on the same finite regular-Cauchy and dyadic tolerance surface. The shared transport does not identify the located and cut presentations by quotient equality; it only preserves the displayed readback rows named by the carrier.
\end{theorem}
\begin{proof}
Start with the located exit. By \autoref{thm:bishop-real-comparison-located-readback}, any located-real consumer first reads the Bishop regular-Cauchy row $B$, then the shared ledger $S$, and then the located row $L$.

Now read the cut-facing exit. By \autoref{thm:bishop-real-comparison-cauchy-dedekind-boundary}, the Dedekind boundary row $D$ is reached through the rational observation and dyadic tolerance rows already named by $S$.

Transport both reads through $H$ and source them through $P,N$. The componentwise $\hsame$ and displayed $\Cont$ rows preserve the visible regular-Cauchy windows, rational readbacks, and dyadic tolerance packets; they do not create a host equality or quotient comparison between the located and cut presentations.

Thus the two exits stay on the same finite surface. The comparison is a shared readback and tolerance transport statement, not a presentation-equivalence theorem.
\end{proof}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_located\_cut\_transport}

\begin{theorem}[BishopRealComparison seal exhaustion]
\label{thm:bishop-real-comparison-seal-exhaustion}
Every $\RealUp$-facing consumer of an accepted $\BishopRealComparisonUp$ packet must first consume the $\StreamNameUp$, $\RegSeqRatUp$, $\DyadicRatCoreUp$, and shared $\RealUp$ seal rows named by $S$ and $R$. No real-facing read can bypass those rows to obtain quotient real equality, host equality, selected limits, trichotomy, or ambient completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BishopRealComparisonUp.BishopRealComparisonPacket\_seal\_exhaustion}
\begin{proof}
Project the shared readback ledger from \autoref{def:bishop-real-comparison-carrier}. The row $S$ names the finite StreamName windows, RegSeqRat rational rows, and DyadicRatCore tolerance packets used by the Bishop, completion, located, and Dedekind-boundary routes.

Apply \autoref{thm:bishop-real-comparison-namecert-obligations} to the seal row. The shared $\RealUp$ seal $R$ is an admitted row only after the finite readback ledger has been exposed.

Apply \autoref{thm:bishop-real-comparison-nonescape} to any attempted real-facing consumer exit. Since quotient real equality, host equality, selected limits, trichotomy, and ambient completeness have no coordinates in the packet, a consumer reaching $R$ still receives only the displayed finite comparison surface.
\end{proof}

\closureat{BishopRealComparisonUp}{seedStr}

\begin{closurestatus}{\BishopRealComparisonUp}
  \constructivestory{A $\BishopRealComparisonUp$ packet is generated from displayed $\BishopRealUp$, $\RealCauchyCompletionUp$, $\LocatedRealUp$, $\DedekindCutUp$, and $\RealUp$ rows, a shared finite readback ledger, componentwise $\hsame$ and $\Cont$ transports, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bishop-real-comparison-carrier}, \autoref{thm:bishop-real-comparison-namecert-obligations}, \autoref{thm:bishop-real-comparison-cauchy-dedekind-boundary}, \autoref{thm:bishop-real-comparison-located-readback}, \autoref{thm:bishop-real-comparison-nonescape}, \autoref{thm:bishop-real-comparison-source-induction}, \autoref{thm:bishop-real-comparison-located-cut-transport}, and \autoref{thm:bishop-real-comparison-seal-exhaustion} bind the comparison packet to a finite comparison surface and non-escape boundary between Bishop, completion-facing, located, and Dedekind-boundary rows and consumers.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close a Lean theorem, bridge checking, quotient-real equality, trichotomy, host real equality, selected limits, ambient completeness, or a global equivalence theorem between Bishop Cauchy names, located reals, and Dedekind cuts.}
  \upgradepath{Obligation closure requires checked carrier admission, comparison boundary transport, located-readback transport, and non-escape theorems over the displayed finite packet; Lean closure requires $\NameCert$ obligations, TasteGate field faithfulness, and a BEDC.Derived.BishopRealComparisonUp carrier and theorem surface matching the displayed finite packet rows, with proofs of the finite comparison, handoff, located-readback, and non-escape rows.}
\end{closurestatus}
