\chapter{A Concrete Naming Certificate for $\BolzanoWeierstrassSelectorUp$}
\label{ch:concrete-instances-bolzanoweierstrassselector-namecert}
\origin{human}

Following Bishop and Bridges, the $\BolzanoWeierstrassSelectorUp$ packet records the finite selector boundary that can be read before any classical Bolzano--Weierstrass conclusion is asserted. The route is anchored by the monotone selector surface of \autoref{ch:concrete-instances-monotone-subsequence-namecert}, the bounded monotone Cauchy witness of \autoref{ch:concrete-instances-boundedmonotonecauchywitness-namecert}, the bounded monotone convergence seal of \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert}, the stream-window interface of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational handoff of \autoref{ch:concrete-instances-regseqrat-namecert}, the dyadic tolerance rows of \autoref{ch:concrete-instances-dyadicratcore-namecert}, and the terminal real-name boundary of \autoref{ch:concrete-instances-real-namecert}. It packages a displayed finite handoff from bounded sequence windows to monotone selected windows, not sequential compactness, a host real completeness theorem, or a choice-selected subsequence.

\begin{definition}[Bolzano--Weierstrass selector carrier]
\label{def:bolzano-weierstrass-selector-carrier}
A $\BolzanoWeierstrassSelectorUp$ carrier is a finite $\BHist$ packet
$$
T=(B,M,Q,W,D,R,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $B$ is the bounded source-sequence window ledger; it records only the finite $\StreamNameUp$ windows currently inspected and the displayed boundedness rows attached to those windows.
\item $M$ is the monotone selector ledger read through $\MonotoneSubsequenceUp$; each displayed entry records a selector position, its source window, and the comparison row that makes the selected window monotone inside the finite packet.
\item $Q$ is the cofinal evidence row for the inspected selector thresholds, limited to thresholds that occur in the packet.
\item $W$ is the selected $\StreamNameUp$ window family obtained from $B,M,Q$.
\item $D$ is the $\DyadicRatCoreUp$ tolerance ledger read from the selected windows before any regular rational or real-facing handoff is available.
\item $R$ is the $\RegSeqRatUp$ handoff row for the selected dyadic windows.
\item $E$ is the $\RealUp$ seal row exposed only through the bounded monotone witness and bounded monotone convergence seal routes after $B,M,Q,W,D,R$ have been displayed.
\item $H$ records componentwise $\hsame$ transport for bounded windows, selector entries, cofinal evidence, selected windows, dyadic rows, regular handoff, Real seal, continuation rows, provenance rows, and local naming rows.
\item $C$ records displayed $\Cont$ routes from $B,M,Q$ to $W$, from $W$ to $D$, from $D$ to $R$, and from the bounded monotone witness and convergence seal packets to $E$.
\item $P$ is the $\Pkg$ provenance over $\BolzanoWeierstrassSelectorUp$, $\MonotoneSubsequenceUp$, $\BoundedMonotoneCauchyWitnessUp$, $\BoundedMonotoneConvergenceSealUp$, $\StreamNameUp$, $\DyadicRatCoreUp$, $\RegSeqRatUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BolzanoWeierstrassSelectorUp}$ row.
\end{enumerate}
The classifier compares accepted packets only through these rows. It has no coordinate for full Bolzano--Weierstrass, sequential compactness, a choice-selected subsequence, quotient-stream equality, host real equality, a least cluster selector, or $\RealUp$ completeness.
\end{definition}

\begin{theorem}[Bolzano--Weierstrass selector subsequence handoff]
\label{thm:bolzano-weierstrass-subsequence-handoff}
Every accepted $\BolzanoWeierstrassSelectorUp$ packet hands bounded source windows to selected monotone windows only through the route
$$
B,M,Q\longmapsto W\longmapsto D\longmapsto R.
$$
The first part of the route factors through $\MonotoneSubsequenceUp$, and the regular-facing handoff is read through $\StreamNameUp$, $\DyadicRatCoreUp$, and $\RegSeqRatUp$ before any $\RealUp$ seal row is consumed.
\end{theorem}
\leanchecked{BEDC.Derived.BolzanoWeierstrassSelectorUp.BolzanoWeierstrassSelectorSubsequenceHandoff}
\begin{proof}
Project the carrier of \autoref{def:bolzano-weierstrass-selector-carrier}. The bounded source row $B$, selector ledger $M$, inspected-threshold cofinality row $Q$, selected windows $W$, dyadic ledger $D$, regular handoff $R$, and structural rows $H,C,P,N$ are the only rows visible before the seal coordinate.

Use the monotone selector surface of \autoref{ch:concrete-instances-monotone-subsequence-namecert}. It identifies the selector ledger and cofinal evidence as finite displayed rows, so the selected windows are obtained by packet replay rather than by countable choice or by an ambient subsequence object.

Next read the selected windows through the terminal finite route. The $\StreamNameUp$ windows provide $W$, the $\DyadicRatCoreUp$ ledger provides $D$, and the $\RegSeqRatUp$ handoff provides $R$.

The transport, continuation, package, and local NameCert rows only preserve this displayed route. Since no other selector coordinate is present, every accepted subsequence handoff factors through $B,M,Q,W,D,R,H,C,P,N$.
\end{proof}

\begin{theorem}[Bolzano--Weierstrass selector Real seal boundary]
\label{thm:bolzano-weierstrass-real-seal-boundary}
Every real-facing read of an accepted $\BolzanoWeierstrassSelectorUp$ packet reaches the seal row $E$ only after the finite selector route
$$
B,M,Q,W,D,R,E
$$
has passed through the bounded monotone Cauchy witness and bounded monotone convergence seal packets. The consumer receives a Real boundary for the selected regular handoff, not full Bolzano--Weierstrass, sequential compactness, a choice-selected subsequence, quotient-stream equality, host real equality, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:bolzano-weierstrass-subsequence-handoff}. It exposes $B,M,Q,W,D,R$ before a Real-facing coordinate can be consumed, and it makes the selected regular handoff the only path from bounded windows to the seal-facing surface.

Now pass through the bounded monotone witness and convergence seal chapters. The witness route of \autoref{ch:concrete-instances-boundedmonotonecauchywitness-namecert} supplies the bounded monotone Cauchy surface, while the seal route of \autoref{ch:concrete-instances-bounded-monotone-convergence-seal-namecert} exposes the Real handoff only after the finite stream, dyadic, regular, and seal rows are displayed.

Finally inspect the excluded data. The carrier has rows for bounded windows, monotone selector entries, cofinal evidence, selected windows, dyadic tolerance rows, a regular handoff, a Real seal, transports, continuations, provenance, and local naming, but it has no row for sequential compactness, arbitrary choice, quotient streams, host equality, or completeness of $\RealUp$.

Thus the Real-facing read is a boundary seal for the displayed finite route and nothing beyond that route is exported.
\end{proof}

\falsifiablePrediction{Every $\BolzanoWeierstrassSelectorUp$ Real-facing read factors through $\MonotoneSubsequenceUp$, $\BoundedMonotoneCauchyWitnessUp$, and $\BoundedMonotoneConvergenceSealUp$ before the $\RealUp$ seal is visible.}

\independenceWitness{monotonesubsequence, boundedmonotonecauchywitness, boundedmonotoneconvergenceseal, streamname, regseqrat, dyadicratcore, real: $\BolzanoWeierstrassSelectorUp$ is not bijective to any listed sibling because it jointly carries bounded sequence windows, a monotone selector ledger, inspected-threshold cofinal evidence, selected stream windows, dyadic tolerance rows, a regular rational handoff, a Real seal boundary, transports, continuations, provenance, and local naming.}

\closureat{BolzanoWeierstrassSelectorUp}{seedStr}

\begin{closurestatus}{\BolzanoWeierstrassSelectorUp}
  \constructivestory{A $\BolzanoWeierstrassSelectorUp$ packet is generated from bounded source windows, a monotone selector ledger, inspected-threshold cofinal evidence, selected StreamName windows, DyadicRatCore tolerance rows, a RegSeqRat handoff, a RealUp seal boundary, componentwise transports, displayed continuations, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bolzano-weierstrass-selector-carrier}, \autoref{thm:bolzano-weierstrass-subsequence-handoff}, and \autoref{thm:bolzano-weierstrass-real-seal-boundary} bind the finite selector carrier, its selected-window handoff, and its Real seal boundary.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not claim full Bolzano-Weierstrass, sequential compactness, choice-selected subsequences, quotient-stream equality, host real equality, RealUp completeness, Lean verification, or bridge checking.}
  \upgradepath{Obligation closure requires checked carrier admission, finite selector stability, inspected-threshold cofinal coverage, selected-window RegSeqRat handoff, bounded monotone witness routing, and Real seal boundary non-escape for BEDC.Derived.BolzanoWeierstrassSelectorUp.}
\end{closurestatus}
