\chapter{A Concrete Naming Certificate for $\BishopIntervalCompactUp$}
\label{ch:concrete-instances-bishop-interval-compact-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\BishopIntervalCompactUp$ packet records the finite-net compact interval surface for displayed real-name intervals. It is anchored in the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite observation windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular-rational readback surface of \autoref{ch:concrete-instances-regseqrat-namecert}, the visible real seal of \autoref{ch:concrete-instances-real-namecert}, the comparison boundary of \autoref{ch:concrete-instances-bishoprealcomparison-namecert}, and the rational witness route of \autoref{ch:concrete-instances-rational-density-real-namecert}. The chapter treats compactness as a finite-net packet over those rows, not as open-cover compactness or a choice-bearing completeness principle.

A $\BishopIntervalCompactUp$ carrier is a finite $\BHist$ packet
$$
K=(A,B,W,T,G,Q,R,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $A$ and $B$ are the lower and upper endpoint names, each read through $\RegSeqRatUp$ rows, finite $\StreamNameUp$ windows, and a visible $\RealUp$ seal.
\item $W$ is the bounded interval window ledger naming the endpoint windows inspected at each dyadic tolerance.
\item $T$ is the $\DyadicRatCoreUp$ tolerance scale used to compare endpoint windows and interval mesh points.
\item $G$ is the finite grid row listing the rational mesh points visible at the chosen dyadic scale.
\item $Q$ is the rational-density witness ledger that routes each mesh cell through $\RationalDensityRealUp$ rather than through host real order.
\item $R$ is the Bishop comparison row recording the same endpoint, readback, and seal surface as a $\BishopRealComparisonUp$ packet.
\item $H$ stores componentwise $\hsame$ transports for endpoints, windows, tolerance, grid, witness, comparison, continuation, package, and local naming rows.
\item $C$ stores the displayed $\Cont$ replay from endpoint windows to dyadic scale, from dyadic scale to grid, and from grid cells to rational witnesses.
\item $P$ is the $\Pkg$ provenance over $\BishopIntervalCompactUp$, $\DyadicRatCoreUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\BishopRealComparisonUp$, $\RationalDensityRealUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\BishopIntervalCompactUp}$ row.
\end{enumerate}

The packet gives a finite interval-net surface: every consumer read factors through the displayed endpoint windows, dyadic tolerance, finite grid, rational-density witnesses, comparison row, transport, continuation, provenance, and local naming. It does not supply a cover selector, a subsequence selector, an ambient Heine--Borel theorem, quotient equality of real names, or a host-real equality test.

\begin{theorem}[BishopIntervalCompact finite-grid obligation]
\label{thm:bishop-interval-compact-finite-grid-obligation}
Let $K=(A,B,W,T,G,Q,R,H,C,P,N)$ be an accepted $\BishopIntervalCompactUp$ carrier. The accepted packet projects the lower endpoint row $A$, the upper endpoint row $B$, the finite $\StreamNameUp$ window ledger $W$, the $\DyadicRatCoreUp$ tolerance scale $T$, the finite rational grid $G$, the $\RationalDensityRealUp$ witness ledger $Q$, the $\BishopRealComparisonUp$ comparison row $R$, the componentwise $\hsame$ transport $H$, the displayed $\Cont$ replay $C$, the $\Pkg$ provenance $P$, and the local $\NameCert_{\BishopIntervalCompactUp}$ row $N$. Every compact-interval read admitted by the packet is exhausted by those rows and by no hidden open-cover, host-real, quotient-equality, or choice-bearing coordinate.
\end{theorem}
\begin{proof}
Project the accepted carrier. Its displayed tuple has exactly the rows $A,B,W,T,G,Q,R,H,C,P,N$, so every endpoint, tolerance, grid, witness, comparison, transport, replay, provenance, and local naming request starts from one of these coordinates.

The finite-grid classifier cannot inspect data outside the displayed tuple. Endpoint reads pass through $A,B,W,T$ and then through the comparison row $R$; mesh reads pass through $T,G,Q$; transport and replay reread the same coordinates through $H$ and $C$.

Since the carrier has no coordinate for a cover selector, a subsequence selector, quotient equality of real names, or host-real equality, a consumer has no route to such data. Thus the accepted compact-interval surface is exhausted by the displayed finite rows.
\end{proof}
\leanchecked{BEDC.Derived.BishopIntervalCompactUp.BishopIntervalCompactTasteGate\_single\_carrier\_alignment}

\begin{theorem}[BishopIntervalCompact rational-density routing]
\label{thm:bishop-interval-compact-rational-density-routing}
For every accepted $\BishopIntervalCompactUp$ carrier $K=(A,B,W,T,G,Q,R,H,C,P,N)$, each mesh-cell witness in $Q$ must route through the rational-density surface of \autoref{ch:concrete-instances-rational-density-real-namecert}, the dyadic tolerance arithmetic of \autoref{ch:concrete-instances-dyadicratcore-namecert}, the finite stream windows of \autoref{ch:concrete-instances-streamname-namecert}, the regular rational readbacks of \autoref{ch:concrete-instances-regseqrat-namecert}, and the visible real seal of \autoref{ch:concrete-instances-real-namecert} before any $\RealUp$-facing seal is visible.
\end{theorem}
\begin{proof}
Begin with a mesh-cell witness named by $Q$. By construction, $Q$ is the rational-density witness ledger for the grid row $G$, so the witness is not a host-real order comparison; it is a displayed $\RationalDensityRealUp$ route attached to the finite mesh cell.

The tolerance requested by the witness is the dyadic row $T$. Its endpoint and mesh reads are inspected through the finite windows $W$, and those windows have regular rational readbacks before they can expose a real-name seal.

The visible seal is therefore reached only after the route has passed through rational density, dyadic tolerance, stream windows, regular rational readback, and the $\RealUp$ certificate surface. Componentwise transport $H$ and continuation replay $C$ preserve this route rather than introducing a separate equality test.
\end{proof}

\begin{theorem}[BishopIntervalCompact compact-metric handoff]
\label{thm:bishop-interval-compact-compact-metric-handoff}
Any compact-metric or interval consumer of an accepted $\BishopIntervalCompactUp$ carrier $K=(A,B,W,T,G,Q,R,H,C,P,N)$ receives only the finite-net packet consisting of endpoint rows, finite windows, dyadic tolerance, finite grid, rational-density witnesses, comparison row, transport, replay, provenance, and local naming. The handoff exports no open-cover compactness, sequential compactness, quotient equality, selected subcover, selected subsequence, countable-choice schedule, or host real equality.
\end{theorem}
\begin{proof}
The consumer boundary is the packet boundary. A downstream compact-metric or interval consumer can read $A,B,W,T,G,Q,R,H,C,P,N$ and can ask the replay row $C$ to reproduce the displayed route from endpoint windows to dyadic tolerance, finite grid, rational witnesses, and comparison rows.

This boundary exports a finite-net object: the grid $G$ is finite, the windows $W$ are displayed, and each witness in $Q$ is routed through the named rational-density and real-seal surfaces. The comparison row $R$ supplies the endpoint boundary without replacing the packet by host equality of real names.

No coordinate of $K$ carries an open cover, an infinite sequence, a selected subcover, a selected subsequence, a quotient-equality proof, or a host-real equality proof. Hence every downstream handoff is a finite-net handoff and not a classical compactness principle.
\end{proof}

\begin{closurestatus}{\BishopIntervalCompactUp}
  \constructivestory{A $\BishopIntervalCompactUp$ packet is generated from displayed endpoint real names, regular-rational readbacks, finite stream windows, a dyadic tolerance scale, a finite rational grid, rational-density witnesses, a Bishop comparison row, componentwise transport, displayed continuation replay, package provenance, and a local $\NameCert$ row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{thm:bishop-interval-compact-finite-grid-obligation}, \autoref{thm:bishop-interval-compact-rational-density-routing}, and \autoref{thm:bishop-interval-compact-compact-metric-handoff} seed the finite-net compact interval packet over the DyadicRatCore, StreamName, RegSeqRat, Real, BishopRealComparison, and RationalDensityReal surfaces.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim open-cover compactness, sequential compactness, Heine--Borel compactness for arbitrary subsets, countable choice, selected limits, or host real equality.}
  \upgradepath{A later verification route can encode the carrier and prove the finite-grid obligation, rational-density routing, compact-metric handoff, comparison-row nonescape, and ledger exactness for the displayed packet.}
\end{closurestatus}
