\chapter{A Concrete Naming Certificate for $\SeparatedMetricUp$}
\label{ch:concrete-instances-separatedmetric-namecert}
\origin{human}

Following Bishop and Bridges, \emph{Constructive Analysis}, the $\SeparatedMetricUp$ packet records the constructive separation surface needed by completion-limit uniqueness. It refines the metric carrier of \autoref{ch:concrete-instances-metric-namecert}, consumes the Cauchy-limit rows of \autoref{ch:concrete-instances-completemetric-namecert}, respects the $\RealUp$ seal boundary of \autoref{ch:concrete-instances-real-namecert}, and reads regular-name comparison through \autoref{ch:concrete-instances-cauchysequenceequivalence-namecert}. The packet treats equality of displayed limit names as a finite classifier consequence of zero-distance observations, not as host equality, trichotomy, quotient formation, open-cover compactness, or ambient real completeness.

\begin{definition}[SeparatedMetric carrier surface]\label{def:separatedmetric-carrier}
A $\SeparatedMetricUp$ carrier is a finite $\BHist$ packet
$$
S=(X,D,Z,L_0,L_1,E,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $X$ is the underlying $\MetricUp$ carrier row, including its point classifier and metric-distance witness surface.
\item $D$ is the $\RealUp$-valued distance witness interface read from metric-distance rows through the displayed real seal.
\item $Z$ is the separation row: whenever two carried observations have displayed zero distance through $D$, the row records the classifier equivalence between the two observations.
\item $L_0$ and $L_1$ are $\CompleteMetricUp$ Cauchy-limit rows for the same regular Cauchy point name, including their displayed moduli and convergence distance ledgers.
\item $E$ is the $\CauchySequenceEquivalenceUp$ comparison route that identifies the two limit claims as readings of one regular Cauchy name through finite windows and dyadic tolerances.
\item $H$ stores componentwise $\hsame$ transport for the metric carrier, real-valued distance witness, separation row, Cauchy-limit rows, equivalence route, continuation row, package row, and local naming row.
\item $C$ stores the $\Cont$ replay from finite Cauchy observations to metric-distance witnesses, from those witnesses to $\RealUp$ zero-distance readings, and from zero-distance readings to the classifier equivalence row.
\item $P$ is the $\Pkg$ provenance over $\MetricUp$, $\RealUp$, $\CompleteMetricUp$, $\CauchySequenceEquivalenceUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$ rows.
\item $N$ is the local $\NameCert_{\SeparatedMetricUp}$ row.
\end{enumerate}
The carrier exposes separatedness only as a finite zero-distance-to-classifier route. It carries no quotient metric-space object, no host equality coordinate, no trichotomy row, no open-cover compactness principle, and no assertion that $\RealUp$ is complete.
\end{definition}
\leandef{BEDC.Derived.SeparatedMetricUp.SeparatedMetricUp}

\begin{definition}[SeparatedMetric classifier surface]\label{def:separatedmetric-classifier}
The classifier of an accepted $\SeparatedMetricUp$ packet relates two carried observations $a,b$ precisely when the packet displays a finite route
$$
a,b\longmapsto \mathsf{MetricDistanceWitness}(a,b,d)\longmapsto D(d,0)\longmapsto Z(a,b).
$$
The first step is a $\MetricUp$ distance-witness row, the second step is a $\RealUp$ zero-distance reading of that witness, and the final step is the separation row identifying $a$ and $b$ inside the point classifier of $X$. Transport of this classifier is componentwise: if $a,b,d,Z(a,b)$ are moved by the stored $\hsame$ rows, then the replayed $\Cont$ path produces the transported zero-distance reading and the transported classifier equivalence.

This classifier is not a quotient-by-equivalence-class construction. It is a local recognition surface for carried observations whose zero-distance evidence is already displayed in the packet.
\end{definition}

\begin{theorem}[SeparatedMetric NameCert obligations]\label{thm:separatedmetric-namecert-obligations}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, the local $\NameCert_{\SeparatedMetricUp}$ surface consists exactly of the following obligations:
\begin{enumerate}
\item carrier admission for the $\MetricUp$ carrier row, $\RealUp$-valued distance witness row, separation row, two $\CompleteMetricUp$ Cauchy-limit rows, $\CauchySequenceEquivalenceUp$ route, componentwise transport, continuation replay, provenance row, and local naming row;
\item classifier stability, stating that zero-distance observations transported by $H$ and replayed by $C$ still yield the transported classifier equivalence through $Z$;
\item completion compatibility, stating that the two limit rows $L_0,L_1$ are read as limits of the same regular Cauchy point name only through the displayed equivalence route $E$;
\item zero-distance exactness, stating that the only route from metric equality evidence to point-classifier equivalence factors through the $\RealUp$ zero-distance witness and the separation row;
\item ledger visibility, stating that the packet exports no quotient metric space, no host equality, no trichotomy, no open-cover compactness, and no $\RealUp$ completeness theorem.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.SeparatedMetricUp.SeparatedMetricPacket\_semantic\_name\_certificate}
\begin{proof}
Carrier admission is the finite tuple of \autoref{def:separatedmetric-carrier}. Every row named in the obligation list is visible in $S$, and no extra equality or compactness row is available to a consumer.

Classifier stability follows from the paired transport and replay rows. The $\hsame$ fields move endpoints, distance witnesses, zero-distance readings, limit rows, and the separation row componentwise, while the $\Cont$ row replays the same finite route after transport.

Completion compatibility reads the two limit rows only through the common regular Cauchy name witnessed by $E$. The route never collapses names into quotient classes; it only shows that both displayed limit claims are attached to one finite-window comparison surface.

Zero-distance exactness is the defining use of the separation row. Once the transported distance witness is read as zero through $D$, the row $Z$ is the unique exported bridge to the point classifier of $X$. The final ledger statement is an inventory check on the fields of $S$.
\end{proof}

\begin{theorem}[SeparatedMetric completion limit uniqueness route]\label{thm:separatedmetric-completion-limit-uniqueness-route}
Let $S$ be an accepted $\SeparatedMetricUp$ packet whose rows $L_0$ and $L_1$ are two $\CompleteMetricUp$ Cauchy-limit witnesses for the same regular Cauchy point name, with sameness displayed by the $\CauchySequenceEquivalenceUp$ route $E$. Then the packet exposes a constructive uniqueness route from the two limit names to the point classifier of the metric carrier:
$$
L_0,L_1\longmapsto E\longmapsto \mathsf{MetricDistanceWitness}(\ell_0,\ell_1,d)\longmapsto D(d,0)\longmapsto Z(\ell_0,\ell_1).
$$
Here $\ell_0$ and $\ell_1$ are the displayed limit histories read from $L_0$ and $L_1$. The conclusion is classifier equivalence inside the carried $\MetricUp$ surface. It is not host equality, not equality of quotient classes, and not an appeal to trichotomy, open-cover compactness, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the two complete-metric limit rows $L_0$ and $L_1$ and use $E$ to keep them attached to the same regular Cauchy point name. The equivalence route supplies the finite-window comparison data needed to compare the two convergence ledgers at a common displayed tolerance.

Replay the metric-distance construction through $C$. The convergence ledgers for $L_0$ and $L_1$ yield a displayed distance witness between the two limit histories; the real-valued distance interface $D$ reads that witness as zero in the packet's $\RealUp$ seal.

Apply the separation row $Z$ to this zero-distance reading. The result is classifier equivalence between $\ell_0$ and $\ell_1$ in the underlying metric carrier $X$.

Each step is a row of $S$ or a replay of a row of $S$. Since quotient classes, host equality, trichotomy, open-cover compactness, and $\RealUp$ completeness are not fields of the packet, none can be used by this route.
\end{proof}

\begin{theorem}[SeparatedMetric Real completion consumer boundary]\label{thm:separatedmetric-real-completion-consumer-boundary}
Every $\RealUp$ or completion consumer of an accepted $\SeparatedMetricUp$ packet can use the packet only through the displayed chain
$$
\MetricUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \RealUp,\ \SeparatedMetricUp .
$$
Concretely, the consumer may read the metric carrier, the two complete-limit rows, the finite-window equivalence route, the real-valued zero-distance witness, the separation row, the componentwise transport rows, the continuation replay, package provenance, and the local naming row. The consumer may not infer quotient metric spaces, host equality of histories, trichotomy of real comparisons, open-cover compactness, or completeness of $\RealUp$ from this packet.
\end{theorem}
\begin{proof}
The carrier inventory in \autoref{def:separatedmetric-carrier} lists exactly the rows available to a consumer. The displayed chain names the order in which those rows can be replayed: metric data first, complete-limit data second, finite-window comparison third, real-valued zero-distance reading fourth, and separation classification last.

The $\hsame$ and $\Cont$ rows preserve this order under transport, so a consumer cannot bypass the zero-distance witness or replace the classifier conclusion with host equality. The package row records only the named BEDC surfaces in the chain.

The non-claims are again field exclusions. No quotient carrier, trichotomy ledger, open-cover compactness row, or $\RealUp$ completeness row occurs in $S$, so no consumer boundary licensed by $N$ can read such a principle from the packet.
\end{proof}

\begin{theorem}[SeparatedMetric zero-distance consumer exactness]
\label{thm:separatedmetric-zero-distance-consumer-exactness}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ packet. Every consumer that reads a zero-distance identification from $S$ must consume, in order, the $\MetricUp$ distance witness in $X$, the $\RealUp$ zero-distance read through $D$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and the local $\NameCert$ row $N$ before the separated classifier row $Z$ may be exported. If the zero-distance read is attached to completion data, the same consumer must first expose the $\CompleteMetricUp$ limit rows $L_0,L_1$ and the $\CauchySequenceEquivalenceUp$ comparison route $E$.

Thus zero-distance consumption is exact at the displayed rows of $S$. It is not host equality, quotient equality, selected representative data, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separatedmetric-carrier}. The metric source is $X$, the real-valued zero-distance witness is $D$, and the classifier export is stored only in the separation row $Z$.

Apply the classifier surface of \autoref{def:separatedmetric-classifier} together with the zero-distance carrier row of \autoref{def:separatedmetric-zero-distance-carrier-row}. These rows force a consumer to form the $\MetricUp$ distance witness before the $\RealUp$ zero-distance read, and to use $Z$ only after that read is displayed.

The structural rows $H,C,P,N$ then transport, replay, source, and name the same finite route. When completion-limit rows are involved, \autoref{thm:separatedmetric-completion-compatibility-scope} inserts $L_0,L_1,E$ before the distance witness is formed.

No other coordinate occurs in $S$. Therefore every accepted zero-distance consumer is exhausted by the displayed route and cannot obtain any excluded equality or completeness principle.
\end{proof}

\begin{theorem}[SeparatedMetric Cauchy uniqueness root package]
\label{thm:separatedmetric-cauchy-uniqueness-root-package}
An accepted $\SeparatedMetricUp$ packet exports completion-limit uniqueness to downstream L10 completion consumers only through the finite package
$$
X,D,Z,L_0,L_1,E,H,C,P,N .
$$
Here $X$ is the metric row, $D$ is the $\RealUp$ zero-distance classifier read, $Z$ is the separated zero-distance classifier, $L_0,L_1$ are the $\CompleteMetricUp$ limit rows, $E$ is the $\CauchySequenceEquivalenceUp$ comparison row, and $H,C,P,N$ are the transport, replay, provenance, and local NameCert rows. The package exports classifier equivalence of the displayed limit names and nothing stronger: no quotient representative, host equality, trichotomy, selected limit, or ambient $\RealUp$ completeness is part of the handoff.
\end{theorem}
\begin{proof}
First use the completion-limit uniqueness route of \autoref{thm:separatedmetric-completion-limit-uniqueness-route}. It reads the two complete-metric limit rows through the same Cauchy-sequence equivalence row before forming the metric-distance witness in $X$.

Next apply \autoref{thm:separatedmetric-zero-distance-consumer-exactness}. That theorem forces every zero-distance consumer to pass through the $\RealUp$ read $D$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and the local naming row $N$ before the separated classifier row $Z$ is exported.

Combining the two routes gives a single root package for downstream completion chapters. Since the accepted packet contains no quotient representative, host-equality coordinate, trichotomy ledger, selected-limit field, or ambient completeness theorem, the exported uniqueness claim remains exactly the displayed separated-classifier handoff.
\end{proof}

\begin{theorem}[SeparatedMetric limit uniqueness scope]
\label{thm:separatedmetric-limit-uniqueness-scope}
For an accepted $\SeparatedMetricUp$ packet $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, every limit-uniqueness claim over the two $\CompleteMetricUp$ rows $L_0,L_1$ is scoped by the route
$$
L_0,L_1 \longmapsto E \longmapsto X \longmapsto D \longmapsto H,C,P,N \longmapsto Z .
$$
Here $E$ is the $\CauchySequenceEquivalenceUp$ comparison route for the two displayed Cauchy presentations, $X$ supplies the $\MetricUp$ distance witness between the two displayed limit histories, $D$ reads that witness as $\RealUp$ zero distance, and $Z$ supplies the separated classifier conclusion. The scope contains no quotient completion equality, host limit equality, selected representative, countable choice, trichotomy, or ambient completeness field.
\end{theorem}
\begin{proof}
Begin with the completion compatibility clause of \autoref{thm:separatedmetric-namecert-obligations}. It requires the two $\CompleteMetricUp$ limit rows to be read through the displayed $\CauchySequenceEquivalenceUp$ route $E$ before their endpoints are compared.

Use the completion limit uniqueness route of \autoref{thm:separatedmetric-completion-limit-uniqueness-route}. After $E$ binds the two limit rows to one regular Cauchy point name, the route forms the metric-distance witness in $X$ and reads it as zero through $D$.

Finally apply \autoref{thm:separatedmetric-zero-distance-consumer-exactness}. The support rows $H,C,P,N$ preserve and name the same route before the classifier row $Z$ is exported. Since the packet has no quotient, host-limit, selected-representative, choice, trichotomy, or ambient-completeness coordinate, the uniqueness claim remains inside this scope.
\end{proof}

\begin{theorem}[SeparatedMetric completion handoff nonescape]
\label{thm:separatedmetric-completion-handoff-nonescape}
Every completion-facing handoff from an accepted $\SeparatedMetricUp$ packet to a downstream L10 consumer must pass through the $\CompleteMetricUp$ limit rows $L_0,L_1$, the $\CauchySequenceEquivalenceUp$ comparison route $E$, the $\MetricUp$ distance witness in $X$, the $\RealUp$ zero-distance read $D$, the separated classifier row $Z$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$. The handoff exports only that routed separated-classifier evidence; it does not export a quotient completion carrier, selected limit, host equality, trichotomy, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with \autoref{thm:separatedmetric-real-completion-consumer-boundary}. It lists the rows a Real or completion consumer may read from the packet and places the complete-limit and finite-window comparison rows before the real zero-distance and separated-classifier rows.

Apply \autoref{thm:separatedmetric-limit-uniqueness-scope}. The limit rows $L_0,L_1$ enter the handoff only through $E$, then through the metric witness in $X$, the zero-distance row $D$, and the classifier row $Z$.

Use \autoref{thm:separatedmetric-zero-distance-consumer-exactness} for the support rows. Transport, replay, provenance, and local naming pass through $H,C,P,N$ and do not add a second carrier or a hidden selector.

The nonescape conclusion is a field inventory. Since no quotient completion, selected limit, host equality, trichotomy, countable-choice, or ambient-completeness row is present in $S$, no downstream completion handoff can read one from the packet.
\end{proof}

\begin{definition}[SeparatedMetric zero-distance carrier row]\label{def:separatedmetric-zero-distance-carrier-row}
The zero-distance carrier row of an accepted $\SeparatedMetricUp$ packet is the displayed $\BHist$ route
$$
\mathsf{MetricDistanceWitness}(a,b,d) \longmapsto \RealUp(d,0) \longmapsto Z(a,b),
$$
where the first term is read from the $\MetricUp$ distance-witness surface of \autoref{def:separatedmetric-carrier}, the middle term is the $\RealUp$ zero-distance row already admitted by the carrier and local NameCert obligations of \autoref{thm:separatedmetric-namecert-obligations}, and $Z(a,b)$ is the separation row consumed by the classifier of \autoref{def:separatedmetric-classifier}. The row is a finite route from a metric-distance witness to point-classifier equivalence. It is not host equality of points, quotient equality, trichotomy of distances, or an ambient completeness assertion for $\RealUp$.
\end{definition}

\begin{theorem}[SeparatedMetric classifier stability row]\label{thm:separatedmetric-classifier-stability-row}
For an accepted $\SeparatedMetricUp$ packet, transported zero-distance evidence replays through the stored $\hsame$ and $\Cont$ rows to the transported point classifier. Concretely, if a displayed route
$$
\mathsf{MetricDistanceWitness}(a,b,d) \longmapsto \RealUp(d,0) \longmapsto Z(a,b)
$$
is transported componentwise by $H$, then $C$ replays the transported distance witness, the transported real zero-distance reading, and the transported separation row before the classifier reads the transported pair.
\end{theorem}
\begin{proof}
Start with the carrier of \autoref{def:separatedmetric-carrier}. Its rows $H$ and $C$ are stored for the metric carrier, real-valued distance witness, separation row, Cauchy-limit rows, equivalence route, continuation row, package row, and local naming row.

Apply classifier stability from \autoref{thm:separatedmetric-namecert-obligations}. The transported endpoints and distance witness first move through the corresponding $\hsame$ fields. The replay row then reads the same zero-distance route through the transported $\RealUp$ row.

Finally apply the classifier surface of \autoref{def:separatedmetric-classifier}. Since the transported zero-distance evidence reaches the transported separation row before classification, the accepted classifier conclusion is the transported point-classifier equivalence and not a host equality or quotient claim.
\end{proof}

\begin{theorem}[SeparatedMetric limit uniqueness ledger]\label{thm:separatedmetric-limit-uniqueness-ledger}
For an accepted $\SeparatedMetricUp$ packet, two $\CompleteMetricUp$ limit rows over the same regular Cauchy name are consumed only through the $\CauchySequenceEquivalenceUp$ route before the separation row is read. In particular, the route
$$
L_0,L_1 \longmapsto E \longmapsto \mathsf{MetricDistanceWitness}(\ell_0,\ell_1,d) \longmapsto \RealUp(d,0) \longmapsto Z(\ell_0,\ell_1)
$$
is the only completion-limit uniqueness ledger exported by the packet.
\end{theorem}
\begin{proof}
Project the two complete-limit rows and the equivalence route from the carrier of \autoref{def:separatedmetric-carrier}. The NameCert obligations of \autoref{thm:separatedmetric-namecert-obligations} require completion compatibility to pass through $E$ before the two limit histories are compared.

Use the completion-limit uniqueness route of \autoref{thm:separatedmetric-completion-limit-uniqueness-route}. It constructs the displayed metric-distance witness between the two limit histories only after $E$ has attached both rows to the same regular Cauchy point name.

The zero-distance carrier row of \autoref{def:separatedmetric-zero-distance-carrier-row} then sends that witness through the $\RealUp$ zero-distance reading and into the separation row. Therefore the exported uniqueness ledger is classifier equivalence through $Z$, with no quotient completion, host equality, selected representative, countable choice, or ambient completeness row.
\end{proof}

\begin{theorem}[SeparatedMetric zero-distance transport]\label{thm:separatedmetric-zero-distance-transport}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ packet. If zero-distance evidence is displayed by the route
$$
\mathsf{MetricDistanceWitness}(a,b,d) \longmapsto \RealUp(d,0) \longmapsto Z(a,b),
$$
then every componentwise transport of this evidence through the stored $\MetricUp$, $\RealUp$, $\hsame$, and $\Cont$ rows yields the transported classifier route for the transported endpoints. The transported route still factors through $X,D,Z,H,C,P,N$ and does not become host equality, quotient equality, or trichotomy of real distances.
\end{theorem}
\begin{proof}
Project the zero-distance row from \autoref{def:separatedmetric-zero-distance-carrier-row}. The displayed evidence starts with a metric-distance witness in $X$, is read as zero through the $\RealUp$ seal row $D$, and reaches the classifier only through the separation row $Z$.

Apply the classifier stability row of \autoref{thm:separatedmetric-classifier-stability-row}. The stored $\hsame$ fields move the endpoints, distance witness, real zero-distance reading, and separation row componentwise, while the stored $\Cont$ row replays the same finite route after transport.

The provenance and local naming rows $P,N$ name this transported route as part of the same packet. Since no host equality coordinate, quotient carrier, or trichotomy ledger occurs in $S$, the transported conclusion remains a $\SeparatedMetricUp$ classifier route and nothing stronger.
\end{proof}

\begin{theorem}[SeparatedMetric completion compatibility scope]\label{thm:separatedmetric-completion-compatibility-scope}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ packet. The two $\CompleteMetricUp$ limit rows $L_0,L_1$ can be compared by the separation row only after both have passed through the displayed $\CauchySequenceEquivalenceUp$ route $E$. Thus every completion-limit uniqueness read has the scoped order
$$
L_0,L_1 \longmapsto E \longmapsto D \longmapsto Z .
$$
No consumer may bypass $E$ by comparing selected representatives, quotient classes, host limit values, or ambient complete-space points.
\end{theorem}
\begin{proof}
Begin with the completion compatibility clause of \autoref{thm:separatedmetric-namecert-obligations}. It states that $L_0$ and $L_1$ are read as two limit rows for one regular Cauchy point name only through the displayed equivalence route $E$.

Use the limit uniqueness ledger of \autoref{thm:separatedmetric-limit-uniqueness-ledger}. That ledger constructs the metric-distance witness between the displayed limit histories only after $E$ has supplied the common finite-window comparison surface.

The zero-distance and classifier steps then use $D$ and $Z$ in that order. The rows $H,C,P,N$ transport, replay, source, and name the same order; they do not add a representative selector or quotient comparison.

Therefore a completion consumer reaches separation only through $E$ first. The absent host-limit, quotient, selected-representative, and ambient-completeness rows cannot supply an alternate comparison scope.
\end{proof}

\begin{theorem}[SeparatedMetric Bishop Cauchy criterion handoff]\label{thm:separatedmetric-bishop-cauchy-criterion-handoff}
Every zero-distance uniqueness consumer of an accepted $\SeparatedMetricUp$ completion carrier must pass through the finite Bishop Cauchy criterion windows of \autoref{ch:concrete-instances-bishop-cauchy-criterion-namecert} before the separated classifier row is exported. The route may then read the existing $\CompleteMetricUp$, $\CauchySequenceEquivalenceUp$, $\MetricUp$, and $\RealUp$ rows of \autoref{thm:separatedmetric-completion-compatibility-scope}, but it exports no quotient equality, selected limit, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Apply \autoref{thm:separatedmetric-completion-compatibility-scope}. It already forces the two completion-limit rows through $E$ before any zero-distance classifier read.

Insert the Bishop Cauchy criterion windows before that equivalence read. The criterion supplies only finite tolerance and stream-window data, so the separated classifier remains a read of $X,D,Z,L_0,L_1,E,H,C,P,N$ and not a host equality or selected-limit export.
\end{proof}

\begin{theorem}[SeparatedMetric completion criterion nonescape]\label{thm:separatedmetric-completion-criterion-nonescape}
If a $\SeparatedMetricUp$ completion-limit uniqueness consumer reads a completion-criterion dependency row, that row must remain between the Bishop Cauchy criterion windows and the regular-name equivalence route before the classifier $Z$ is exported. The dependency can be consumed through the completion siblings, but it does not supply quotient equality, selected representatives, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-bishop-cauchy-criterion-handoff} for the finite Cauchy windows and \autoref{thm:separatedmetric-completion-compatibility-scope} for the ordered route through $E,D,Z$.

The completion-criterion row is therefore a dependency inside the finite route, not an additional equality principle. Since the carrier has no coordinate for quotient comparison, selected representatives, choice, or ambient completeness, the separated classifier can only be exported after the dependency has been replayed through $H,C,P,N$.
\end{proof}

\begin{theorem}[SeparatedMetric regular-name uniqueness exhaustion]\label{thm:separatedmetric-regular-name-uniqueness-exhaustion}
The regular-name uniqueness surface for an accepted $\SeparatedMetricUp$ completion carrier is exhausted by Bishop Cauchy criterion windows, the completion-criterion dependency row, the $\CauchySequenceEquivalenceUp$ route, the $\RealUp$ zero-distance witness, and the separated classifier row. No downstream consumer obtains a second uniqueness route from quotient equality, a selected limit, countable choice, or ambient Real completeness.
\end{theorem}
\begin{proof}
Project the completion carrier and apply \autoref{thm:separatedmetric-bishop-cauchy-criterion-handoff} and \autoref{thm:separatedmetric-completion-criterion-nonescape}. These force the finite criterion, completion dependency, and regular-name equivalence rows to precede the classifier export.

The remaining rows $H,C,P,N$ only transport, replay, source, and name that same route. Thus the listed rows exhaust regular-name uniqueness before separation, and the excluded principles have no carrier row from which a consumer could read them.
\end{proof}

\begin{definition}[SeparatedMetric zero-distance scope row]
\label{def:separatedmetric-zero-distance-scope-row}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, the zero-distance scope row is the finite route that begins with a $\MetricUp$ distance witness in $X$, reads the witness as a $\RealUp$ zero-distance row through $D$, transports the evidence through $H$, replays it through $C$, sources it through $P$, names it through $N$, and only then exports the classifier equivalence supplied by $Z$. If the zero-distance read is attached to completion-limit data, the route first passes through the $\CauchySequenceEquivalenceUp$ row $E$ that binds $L_0$ and $L_1$ to the same regular Cauchy point name.

The row is a scope obligation for displayed evidence. It is not host point equality, quotient real equality, a selected representative, trichotomy, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[SeparatedMetric zero-distance reflection]
\label{thm:separatedmetric-zero-distance-reflection}
Every classifier equivalence exported by a zero-distance read from an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ reflects the route of \autoref{def:separatedmetric-zero-distance-scope-row}. In particular, the export must pass through a $\MetricUp$ distance witness, the $\RealUp$ zero-distance row $D$, the componentwise $\hsame$ transport $H$, the displayed $\Cont$ replay $C$, the $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$ before the classifier row $Z$ is available.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separatedmetric-carrier}. The metric source is $X$, the real-valued distance interface is $D$, and the classifier export is stored only in the separation row $Z$.

Apply the zero-distance scope row of \autoref{def:separatedmetric-zero-distance-scope-row}. It places the distance witness before the $\RealUp$ zero-distance read and places the support rows $H,C,P,N$ before the classifier export.

Use \autoref{thm:separatedmetric-classifier-stability-row} to transport and replay the same route. The resulting classifier equivalence is therefore a reflected BEDC row, not host equality, quotient equality, selected representative data, trichotomy, or a completeness principle.
\end{proof}

\begin{theorem}[SeparatedMetric completion-limit uniqueness scope]
\label{thm:separatedmetric-completion-limit-uniqueness-scope}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Any completion-limit uniqueness claim exported from $S$ must read $L_0$ and $L_1$ through the $\CauchySequenceEquivalenceUp$ row $E$ before it can form the $\MetricUp$ distance witness, read $\RealUp$ zero-distance through $D$, transport through $H$, replay through $C$, source through $P$, name through $N$, and export classifier equivalence through $Z$.

Consequently completion-limit uniqueness is scoped as classifier equivalence in the displayed metric carrier. It is not host limit equality, quotient real equality, quotient completion equality, a selected representative, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:separatedmetric-completion-compatibility-scope}. It requires the two complete-metric limit rows to pass through $E$ before the separation row can be read.

Next apply \autoref{thm:separatedmetric-limit-uniqueness-ledger}. The ledger constructs the metric-distance witness only after the finite-window equivalence route has tied the two limit rows to the same regular Cauchy point name.

Finally use \autoref{thm:separatedmetric-zero-distance-reflection}. The zero-distance evidence travels through $D,H,C,P,N$ before $Z$ exports classifier equivalence. Since no host equality, quotient equality, selected representative, trichotomy, or completeness field occurs in $S$, the uniqueness claim remains inside the displayed classifier scope.
\end{proof}

\begin{theorem}[SeparatedMetric real zero-distance nonescape]
\label{thm:separatedmetric-real-zero-distance-nonescape}
For every accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, a $\RealUp$ zero-distance read can be consumed only as part of the finite route through $\MetricUp$ distance witnesses, $\CauchySequenceEquivalenceUp$ when completion-limit rows are present, componentwise $\hsame$, displayed $\Cont$, $\Pkg$, and $\NameCert$. The $\RealUp$ row supplies the zero-distance witness used by $Z$; it does not export host real equality, quotient real equality, trichotomy, selected representatives, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Read the zero-distance scope row from \autoref{def:separatedmetric-zero-distance-scope-row}. It places the $\RealUp$ row after the metric-distance witness and before the separation classifier.

If completion-limit rows are involved, use \autoref{thm:separatedmetric-completion-limit-uniqueness-scope}. The route first passes through $E$, then the distance witness, then $D$, and only afterward the transport, replay, provenance, naming, and classifier rows.

The nonescape statement is the field inventory of $S$. The carrier contains no host real equality row, quotient real equality row, trichotomy ledger, selected representative coordinate, or ambient completeness theorem, so the zero-distance read cannot export any of them.
\end{proof}

\begin{theorem}[SeparatedMetric consumer nonescape scope]\label{thm:separatedmetric-consumer-nonescape-scope}
Every accepted consumer of a $\SeparatedMetricUp$ packet receives only the rows
$$
\MetricUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \RealUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Consequently the consumer may inspect metric distance evidence, two complete-limit rows, their finite-window equivalence route, the real zero-distance seal, componentwise transport, replay, provenance, and local naming, but no quotient carrier, host equality, trichotomy row, selected representative, open-cover compactness principle, or $\RealUp$ completeness theorem.
\end{theorem}
\begin{proof}
Read the carrier inventory in \autoref{def:separatedmetric-carrier}. Its visible fields are the metric carrier row $X$, the real-valued distance row $D$, the separation row $Z$, the two complete-limit rows $L_0,L_1$, the equivalence route $E$, and the support rows $H,C,P,N$.

The consumer boundary theorem, \autoref{thm:separatedmetric-real-completion-consumer-boundary}, gives the permitted order of access. Consumers read metric data, complete-limit data, finite-window equivalence, real zero-distance evidence, and separation classification through the displayed support rows.

The nonescape conclusion is then a field-exhaustion claim. Since the carrier has no quotient object, host equality predicate, trichotomy ledger, selected representative, open-cover compactness coordinate, or $\RealUp$ completeness coordinate, no accepted consumer route can recover any of those objects from $N$.
\end{proof}

\begin{theorem}[SeparatedMetric zero-distance scope]\label{thm:separatedmetric-zero-distance-scope}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier as in \autoref{def:separatedmetric-carrier}. Every zero-distance transport accepted by the local $\NameCert_{\SeparatedMetricUp}$ row is a displayed $\BHist$ route
$$
\mathsf{MetricDistanceWitness}(a,b,d) \longmapsto D(d,0) \longmapsto Z(a,b)
$$
carried by $X,D,Z,H,C,P,N$. Transport by $\hsame$ and replay by $\Cont$ preserve this route before the point classifier is read, so the downstream zero-distance consumer receives classifier equivalence and not host equality, quotient equality, trichotomy, or an ambient $\RealUp$ completeness principle.
\end{theorem}
\begin{proof}
Project the displayed packet from \autoref{def:separatedmetric-carrier}. The rows available for zero-distance transport are the metric carrier $X$, the real-valued distance interface $D$, the separation row $Z$, and the support rows $H,C,P,N$.

Use the zero-distance carrier row of \autoref{def:separatedmetric-zero-distance-carrier-row}. It fixes the order of the route: metric-distance witness first, real zero-distance reading second, and separation classification third.

Now apply the transported classifier stability row of \autoref{thm:separatedmetric-classifier-stability-row}. The $\hsame$ fields move the displayed histories componentwise and the $\Cont$ field replays the same route after transport.

Since the packet has no host equality coordinate, quotient carrier, trichotomy ledger, or completeness row, the transported conclusion remains exactly the classifier route named by $N$.
\end{proof}

\begin{theorem}[SeparatedMetric limit route scope]\label{thm:separatedmetric-limit-route-scope}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. A completion-limit uniqueness read from $S$ can inspect the two $\CompleteMetricUp$ rows $L_0,L_1$ only after the $\BHist$ comparison route $E$ has displayed that both rows belong to the same regular Cauchy point name. The accepted downstream route is therefore
$$
L_0,L_1 \longmapsto E \longmapsto \mathsf{MetricDistanceWitness}(\ell_0,\ell_1,d) \longmapsto D(d,0) \longmapsto Z(\ell_0,\ell_1),
$$
with transport and replay supplied only by $H$ and $C$ and with provenance and local naming supplied only by $P$ and $N$.
\end{theorem}
\begin{proof}
Read $L_0,L_1,E$ from the carrier of \autoref{def:separatedmetric-carrier}. The comparison route $E$ is the only displayed row tying the two complete-metric limit claims to one regular Cauchy point name.

Apply \autoref{thm:separatedmetric-completion-compatibility-scope}. It places the equivalence route before the real zero-distance row and before the separation row, ruling out representative comparison or quotient-class comparison as an alternate path.

Then use \autoref{thm:separatedmetric-limit-uniqueness-ledger}. The ledger constructs the metric-distance witness between the displayed limit histories after $E$ has fixed the common finite-window comparison surface.

The final zero-distance and classifier reads go through $D$ and $Z$. Rows $H,C,P,N$ only preserve and name that same route, so the completion-limit consumer receives uniqueness as classifier equivalence inside $X$, not as host equality or selected completion data.
\end{proof}

\begin{theorem}[SeparatedMetric classifier ledger scope]\label{thm:separatedmetric-classifier-ledger-scope}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, the classifier ledger exported by $\NameCert_{\SeparatedMetricUp}$ is exhausted by
$$
\MetricUp,\ \RealUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Every accepted consumer must read metric evidence, real zero-distance evidence, complete-limit rows, the finite-window equivalence route, componentwise transport, continuation replay, provenance, and local naming through these rows. No ledger entry permits escape to quotient metric spaces, host equality of histories, selected representatives, trichotomy, open-cover compactness, or $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the carrier inventory of \autoref{def:separatedmetric-carrier}. It lists exactly the metric row $X$, real-valued distance row $D$, separation row $Z$, complete-limit rows $L_0,L_1$, equivalence route $E$, and structural rows $H,C,P,N$.

The NameCert obligations of \autoref{thm:separatedmetric-namecert-obligations} then partition these rows into carrier admission, classifier stability, completion compatibility, zero-distance exactness, and ledger visibility. Each obligation is anchored in the displayed $\BHist$ packet.

Use the consumer nonescape theorem \autoref{thm:separatedmetric-consumer-nonescape-scope}. It states that downstream access remains inside the listed metric, completion, equivalence, real, transport, replay, provenance, and naming rows.

Thus the classifier ledger has no unlisted escape row. Quotient metric spaces, host equality, selected representatives, trichotomy, open-cover compactness, and $\RealUp$ completeness are not fields of $S$ and cannot be read from its local naming row.
\end{proof}

\closureat{SeparatedMetricUp}{obligationStr}

\begin{theorem}[SeparatedMetric zero-distance NameCert readiness]
\label{thm:separatedmetric-zero-distance-namecert-readiness}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, the zero-distance obligation exported to $\NameCert_{\SeparatedMetricUp}$ is exactly the finite $\BHist$ route through
$$
\MetricUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
It reads metric evidence from $X$, the real zero-distance seal from $D$, classifier separation from $Z$, and transport, replay, provenance, and local naming from $H,C,P,N$; it does not expose host equality, quotient equality, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separatedmetric-carrier}. The visible zero-distance rows are the metric carrier $X$, the real-valued distance row $D$, and the separation row $Z$.

Use the zero-distance carrier row of \autoref{def:separatedmetric-zero-distance-carrier-row} and the transported classifier stability row of \autoref{thm:separatedmetric-classifier-stability-row}. They force every zero-distance read through the displayed metric witness, the $\RealUp$ zero-distance reading, and the classifier row, with $H$ and $C$ preserving the same route.

The provenance and local naming rows $P,N$ then package the route as a NameCert obligation. Since the carrier contains no host equality or quotient coordinate, the readiness claim remains a finite classifier route.
\end{proof}

\begin{theorem}[SeparatedMetric completion-limit equivalence handoff]
\label{thm:separatedmetric-completion-limit-equivalence-handoff}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every completion-limit comparison exported by $S$ must first pass through
$$
\CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \MetricUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
Thus the two completion limit rows $L_0,L_1$ are handed to the separation row only after the finite equivalence route $E$ identifies the common regular Cauchy point name.
\end{theorem}
\begin{proof}
Read the two complete-limit rows and the equivalence route from \autoref{def:separatedmetric-carrier}. The packet stores $L_0,L_1,E$ as finite rows, not as selected completion representatives.

Apply \autoref{thm:separatedmetric-limit-uniqueness-ledger} and \autoref{thm:separatedmetric-limit-route-scope}. Together they place $E$ before the metric-distance witness, the real zero-distance row, and the separation classifier.

Finally use \autoref{thm:separatedmetric-classifier-ledger-scope}. The support rows $H,C,P,N$ preserve and name the same handoff, and no quotient completion, host equality, countable choice, or ambient completeness row is available.
\end{proof}

\begin{theorem}[SeparatedMetric Real-seal boundary obligations]
\label{thm:separatedmetric-real-seal-boundary-obligations}
For an accepted $\SeparatedMetricUp$ carrier, every $\RealUp$-facing boundary read in a zero-distance or completion-limit obligation is exhausted by the rows
$$
\MetricUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \RealUp,\ \BHist,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
The $\RealUp$ row supplies only the displayed zero-distance seal used by the classifier; it does not supply real completeness, quotient equality of completion names, trichotomy, selected representatives, or open-cover compactness.
\end{theorem}
\begin{proof}
Start from \autoref{thm:separatedmetric-zero-distance-namecert-readiness}. It identifies the real-facing zero-distance route as a finite metric witness followed by the $\RealUp$ zero seal and the separation classifier.

Then use \autoref{thm:separatedmetric-completion-limit-equivalence-handoff}. Completion-limit comparisons reach the real seal only after the $\CauchySequenceEquivalenceUp$ row has tied both complete-metric limit rows to the same regular Cauchy name.

The boundary conclusion follows from \autoref{thm:separatedmetric-consumer-nonescape-scope}. All accepted reads are carried by $\BHist$, transported by $\hsame$, replayed by $\Cont$, and named through $\Pkg$ and $\NameCert$, with no field for a stronger host-side principle.
\end{proof}

\begin{theorem}[SeparatedMetric kernel zero-distance obligation]
\label{thm:separatedmetric-kernel-zero-distance-obligation}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, every zero-distance classifier obligation exported by the kernel factors through the route
$$
\MetricUp \longmapsto \RealUp \longmapsto \hsame \longmapsto \Cont \longmapsto \Pkg \longmapsto \NameCert .
$$
The $\MetricUp$ distance witness is read before the $\RealUp$ zero row, and only after transport, replay, provenance, and local naming may the classifier row $Z$ expose separation equivalence. The obligation exports no host equality, quotient equality, selected representative, trichotomy row, or ambient completeness principle.
\end{theorem}
\begin{proof}
Read the zero-distance carrier row of \autoref{def:separatedmetric-zero-distance-carrier-row}. It fixes the route from a displayed metric-distance witness to the $\RealUp$ zero row and then to the separation classifier.

Next apply the transported classifier stability row of \autoref{thm:separatedmetric-classifier-stability-row}. The $\hsame$ and $\Cont$ rows preserve the same displayed route after transport, while $P$ and $N$ source and name it as a local certificate obligation.

The nonescape clause is immediate from the carrier inventory in \autoref{def:separatedmetric-carrier}. None of the excluded host or quotient principles is a coordinate of $S$.
\end{proof}

\begin{theorem}[SeparatedMetric completion-equivalence obligation]
\label{thm:separatedmetric-completion-equivalence-obligation}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Any completion-equivalence obligation that compares the two $\CompleteMetricUp$ limit rows $L_0,L_1$ must first pass through the $\CauchySequenceEquivalenceUp$ route $E$ before the separation row can read a metric-distance witness, the $\RealUp$ zero seal, transport, replay, provenance, and local naming.

Thus the separated completion consumer receives only classifier equivalence inside the displayed metric carrier. It does not receive quotient completion equality, selected representatives, host limit equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with \autoref{thm:separatedmetric-completion-compatibility-scope}. It places the finite-window equivalence route $E$ before any zero-distance or separation read involving $L_0$ and $L_1$.

Then use \autoref{thm:separatedmetric-limit-route-scope}. After $E$ has tied the complete-metric rows to one regular Cauchy point name, the route may construct the displayed metric-distance witness and read the $\RealUp$ zero seal through $D$.

Finally apply \autoref{thm:separatedmetric-classifier-ledger-scope}. The rows $H,C,P,N$ transport, replay, source, and name the same route, so no quotient completion object or stronger host-side equality is exported.
\end{proof}

\begin{theorem}[SeparatedMetric Real-seal routing obligation]
\label{thm:separatedmetric-real-seal-obligation}
For an accepted $\SeparatedMetricUp$ carrier, the $\RealUp$ row in every zero-distance or completion-equivalence route is only a seal inside the finite certificate route
$$
\MetricUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \RealUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
It certifies the displayed zero-distance read consumed by $Z$; it does not supply $\RealUp$ completeness, quotient equality of real names, quotient equality of completion names, trichotomy, or selected representative data.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-real-seal-boundary-obligations}. The real-facing row is reached only after the relevant metric or completion-equivalence rows have been displayed.

For a pure zero-distance route, \autoref{thm:separatedmetric-kernel-zero-distance-obligation} places the $\RealUp$ row between the metric-distance witness and the classifier. For a completion route, \autoref{thm:separatedmetric-completion-equivalence-obligation} first inserts the $\CauchySequenceEquivalenceUp$ row between the complete-metric limits and the zero-distance read.

In both cases the support rows $H,C,P,N$ preserve and name the same finite route. Since no Real completeness, quotient equality, trichotomy, or representative-selection coordinate is present, the Real row remains a seal and not an escape principle.
\end{proof}

\begin{theorem}[SeparatedMetric root zero-distance dependency]
\label{thm:separatedmetric-root-zero-distance-dependency}
Every accepted $\SeparatedMetricUp$ consumer that exposes the separated classifier must first pass through the root $\MetricUp$ distance dependency. For a carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, the row $X$ supplies the displayed metric source and distance witness, $D$ seals that witness as a $\RealUp$ zero-distance row, and only then may $Z$ expose the separated classifier through $H,C,P,N$.

The consumer receives no classifier route from host equality, quotient metric equality, selected representatives, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier tuple. The only coordinate naming the metric source and distance witness is $X$, so every classifier read begins there.

Apply \autoref{thm:separatedmetric-kernel-zero-distance-obligation}. It places the $\MetricUp$ distance row before the $\RealUp$ zero seal and the separated classifier.

Finally use the support rows $H,C,P,N$ to transport, replay, source, and name the same route. Since the carrier has no extra host-equality or quotient coordinate, the exposed classifier is dependent on the displayed zero-distance route.
\end{proof}

\begin{theorem}[SeparatedMetric root completion-equivalence dependency]
\label{thm:separatedmetric-root-completion-equivalence-dependency}
Every accepted completion-facing $\SeparatedMetricUp$ consumer must pass through the $\CauchySequenceEquivalenceUp$ route $E$ and the $\CompleteMetricUp$ limit rows $L_0,L_1$ before exposing the separated classifier. The completion-equivalence dependency is therefore the finite route
$$
L_0,L_1,E,X,D,Z,H,C,P,N
$$
inside the accepted carrier, not a quotient completion equality or a selected host limit.
\end{theorem}
\begin{proof}
Begin with the completion rows $L_0,L_1$. They are the only packet coordinates that can serve a completion-facing consumer.

Use \autoref{thm:separatedmetric-completion-equivalence-obligation}. It forces any comparison of $L_0$ and $L_1$ through the finite-window route $E$ before the metric-distance and zero-seal rows may be read.

Then apply \autoref{thm:separatedmetric-root-zero-distance-dependency}. The separated classifier is exposed only after $X,D,Z$ and the support rows have been consumed, so the completion-equivalence dependency cannot escape into quotient completion equality, countable choice, or selected limits.
\end{proof}

\begin{theorem}[SeparatedMetric root Real-seal dependency]
\label{thm:separatedmetric-root-real-seal-dependency}
Every accepted Real-facing $\SeparatedMetricUp$ consumer must pass through the root $\RealUp$ zero-seal row $D$ before it exposes the separated classifier. In the zero-distance branch this dependency is $X,D,Z,H,C,P,N$; in the completion branch it is $L_0,L_1,E,X,D,Z,H,C,P,N$.

Thus the Real row is a dependency of the separated classifier, not an independent source of Real completeness, quotient equality of real names, quotient equality of completion names, trichotomy, or representative selection.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-real-seal-obligation}. It identifies the $\RealUp$ row as a zero-distance seal inside each accepted zero-distance or completion-equivalence route.

For the zero-distance branch, apply \autoref{thm:separatedmetric-root-zero-distance-dependency}. For the completion branch, apply \autoref{thm:separatedmetric-root-completion-equivalence-dependency}.

Both branches reach the same classifier row $Z$ only after $D$ has been read and after $H,C,P,N$ have transported and named the displayed route. The carrier contains no independent Real-completeness or quotient-equality coordinate, so the Real seal remains a dependency boundary.
\end{proof}

\begin{theorem}[SeparatedMetric root classifier transport obligation]
\label{thm:separatedmetric-root-classifier-transport-obligation}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. The root classifier transport obligation has exactly the $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$ surface displayed by $H,C,P,N$: any transported classifier read must first expose the carrier row of \autoref{def:separatedmetric-carrier}, the zero-distance dependency of \autoref{thm:separatedmetric-root-zero-distance-dependency}, the completion-equivalence dependency of \autoref{thm:separatedmetric-root-completion-equivalence-dependency}, and the Real-seal dependency of \autoref{thm:separatedmetric-root-real-seal-dependency}.

Consequently the classifier cannot be transported by host equality, quotient metric equality, selected completion representatives, countable choice, trichotomy, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier. The classifier coordinate $Z$ is not a free equality row; it is downstream of the metric source $X$, the zero-distance row $D$, the completion route $E$ when completion rows are read, and the support rows $H,C,P,N$.

Use \autoref{thm:separatedmetric-root-zero-distance-dependency} for the pure metric branch and \autoref{thm:separatedmetric-root-completion-equivalence-dependency} for the completion branch. Both branches pass through the same zero-distance classifier route before the separated classifier is exposed.

Finally apply \autoref{thm:separatedmetric-root-real-seal-dependency}. Since the $\RealUp$ row remains a seal inside the displayed route, transport through $\hsame$ and replay through $\Cont$ can rename only the finite $\BHist$ rows already packaged by $P,N$.
\end{proof}

\begin{theorem}[SeparatedMetric root completion readback obligation]
\label{thm:separatedmetric-root-completion-readback-obligation}
For every accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, a completion-facing readback of the separated classifier must pass through the displayed $\CompleteMetricUp$ rows $L_0,L_1$, the $\CauchySequenceEquivalenceUp$ dependency $E$, the zero-distance dependency row, and the $\RealUp$ seal before $H,C,P,N$ name it as a $\BHist$ and $\NameCert$ obligation.

The readback does not export quotient completion equality, a selected limit representative, host limit equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the carrier and classifier inventory in \autoref{def:separatedmetric-carrier}. The only completion rows available to a consumer are $L_0,L_1$ and the displayed equivalence route $E$.

Apply \autoref{thm:separatedmetric-root-completion-equivalence-dependency}. It forces completion-facing comparison through $E$ before the zero-distance and classifier rows can be read.

Then use \autoref{thm:separatedmetric-root-classifier-transport-obligation}. The readback is transported only by $H$ and replayed only by $C$, while $P,N$ package the same route as a local NameCert row, so no completion quotient or selected representative is exposed.
\end{proof}

\begin{theorem}[SeparatedMetric root Real-seal nonescape obligation]
\label{thm:separatedmetric-root-real-seal-nonescape-obligation}
Every Real-facing root obligation of an accepted $\SeparatedMetricUp$ carrier is exhausted by the finite route through the carrier, the zero-distance dependency row, the completion-equivalence dependency row when present, the $\RealUp$ seal, and the support surface $\BHist,\hsame,\Cont,\Pkg,\NameCert$. The Real seal is therefore a boundary row for the separated classifier, not a source of quotient real equality, quotient completion equality, trichotomy, selected representatives, or ambient real completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-root-real-seal-dependency}. It places the Real row after the metric-distance witness in the zero-distance branch and after the completion-equivalence handoff in the completion branch.

For the zero-distance route, apply \autoref{thm:separatedmetric-root-zero-distance-dependency}. For the completion route, apply \autoref{thm:separatedmetric-root-completion-readback-obligation}. These two rows cover the only classifier-facing branches present in \autoref{def:separatedmetric-carrier}.

The rows $H,C,P,N$ then transport, replay, source, and name the same finite route. Since the carrier contains no coordinate for the excluded host principles, the Real seal cannot escape its displayed obligation boundary.
\end{proof}

\begin{theorem}[SeparatedMetric public identity export]
\label{thm:separatedmetric-public-identity-export}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every public identity consumer that asks when two displayed points of $X$ are identified must read the metric-distance witness through $D$, the $\RealUp$ zero seal, and the separation classifier $Z$ before exposing an identity claim. The exported claim is exactly the zero-distance route of \autoref{thm:separatedmetric-kernel-zero-distance-obligation}; it carries no host equality, quotient equality, selected representative, trichotomy row, or ambient completeness principle.
\end{theorem}
\begin{proof}
Project the carrier $S$. The only identity-facing rows are the metric row $X$, the distance and zero-seal route $D$, the classifier $Z$, and the structural rows $H,C,P,N$.

Apply \autoref{thm:separatedmetric-kernel-zero-distance-obligation}. It places the metric-distance witness before the $\RealUp$ zero row and places both before the separation classifier.

Finally use \autoref{thm:separatedmetric-consumer-nonescape-scope}. The support rows transport, replay, source, and name the same route, so the public identity export cannot detach into host equality or a quotient principle.
\end{proof}

\begin{theorem}[SeparatedMetric public completion uniqueness export]
\label{thm:separatedmetric-public-completion-uniqueness-export}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every public completion-uniqueness consumer comparing the completion rows $L_0$ and $L_1$ must first read the $\CauchySequenceEquivalenceUp$ route $E$ and then the zero-distance classifier route through $D,Z,H,C,P,N$. The export is the completion-equivalence boundary of \autoref{thm:separatedmetric-completion-equivalence-obligation}; it supplies no quotient completion equality, selected limit, host limit equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start from the completion rows $L_0$ and $L_1$ in the carrier. They are not public equality rows by themselves; they are complete-metric limit rows tied to the displayed route $E$.

Apply \autoref{thm:separatedmetric-completion-equivalence-obligation}. It forces any comparison of $L_0$ and $L_1$ through $E$ before the route may read the zero-distance witness and separation classifier.

Then use \autoref{thm:separatedmetric-completion-limit-equivalence-handoff} and \autoref{thm:separatedmetric-limit-route-scope}. These keep the completion comparison inside the finite Cauchy-equivalence and zero-distance handoff.

The rows $H,C,P,N$ provide only transport, replay, provenance, and local naming. Therefore the public uniqueness export is exhausted by the displayed separated-metric route.
\end{proof}

\begin{theorem}[SeparatedMetric public Real-seal nonescape export]
\label{thm:separatedmetric-public-real-seal-nonescape-export}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every public $\RealUp$-seal consumer of a zero-distance or completion-uniqueness route receives the seal only inside
$$
\MetricUp,\ \CompleteMetricUp,\ \CauchySequenceEquivalenceUp,\ \RealUp,\ \hsame,\ \Cont,\ \Pkg,\ \NameCert .
$$
The exported Real-facing boundary is the nonescape route of \autoref{thm:separatedmetric-real-seal-obligation}; it does not provide Real completeness, quotient equality of real names, quotient equality of completion names, trichotomy, or representative selection.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-real-seal-obligation}. It states that the $\RealUp$ row is only the displayed zero-distance seal inside the finite certificate route.

For identity consumers, apply \autoref{thm:separatedmetric-public-identity-export}. For completion-uniqueness consumers, apply \autoref{thm:separatedmetric-public-completion-uniqueness-export}. These two exports account for the public zero-distance and completion-facing routes.

Since the same support rows $H,C,P,N$ preserve both routes, no public consumer can reinterpret the Real seal as a stronger host-side principle.
\end{proof}

\begin{theorem}[SeparatedMetric zero-distance separation obligation]
\label{thm:separatedmetric-zero-distance-separation-obligation}
For every accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, any bridge-facing zero-distance separation read must pass through the $\MetricUp$ carrier row $X$, the $\RealUp$-valued distance witness row $D$, and the separation classifier row $Z$ before the structural rows $H,C,P,N$ can expose it to a public consumer. The route is a finite projection from the displayed carrier; it is not host equality, quotient equality, trichotomy, representative selection, or ambient completeness.
\end{theorem}
\begin{proof}
Project $S$ through \autoref{def:separatedmetric-carrier}. The only rows that can answer a zero-distance separation request are $X,D,Z$ and the structural rows attached to them.

Apply \autoref{thm:separatedmetric-kernel-zero-distance-obligation}. It places the $\MetricUp$ distance witness before the $\RealUp$ zero-distance reading and places both before the separation classifier.

The bridge-facing consumer then receives the transported and replayed route through $H,C,P,N$. Since no excluded host-side principle is a carrier row, the bridge surface remains a finite projection.
\end{proof}

\begin{theorem}[SeparatedMetric completion uniqueness obligation]
\label{thm:separatedmetric-completion-uniqueness-obligation}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Any bridge-facing completion-uniqueness read comparing the two $\CompleteMetricUp$ rows $L_0,L_1$ must first use the $\CauchySequenceEquivalenceUp$ route $E$, then the zero-distance route through $X,D,Z$, and finally the structural rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Start with the public completion uniqueness export of \autoref{thm:separatedmetric-public-completion-uniqueness-export}. It fixes $E$ as the required route from the two complete-metric limit rows to a common finite-window comparison.

Use \autoref{thm:separatedmetric-completion-equivalence-obligation}. After $E$ is displayed, the comparison may read the metric-distance witness, the $\RealUp$ zero seal, and the separation row.

The rows $H,C,P,N$ transport, replay, source, and name this same finite chain. Hence the bridge-facing uniqueness obligation exports no quotient completion equality, selected limit, host equality, countable choice, or ambient $\RealUp$ completeness.
\end{proof}

\begin{theorem}[SeparatedMetric Real-seal nonescape obligation]
\label{thm:separatedmetric-real-seal-nonescape-obligation}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, every bridge-facing $\RealUp$ seal read is confined to the displayed zero-distance or completion-uniqueness route through $\MetricUp$, $\CompleteMetricUp$, $\CauchySequenceEquivalenceUp$, $\RealUp$, $H,C,P,N$. It does not export $\RealUp$ completeness, quotient equality of real names, quotient equality of completion names, trichotomy, or representative selection.
\end{theorem}
\begin{proof}
Apply the public Real-seal nonescape export of \autoref{thm:separatedmetric-public-real-seal-nonescape-export}. It already identifies the Real row as a zero-distance seal inside the finite separated-metric route.

For the identity branch, use \autoref{thm:separatedmetric-zero-distance-separation-obligation}. For the completion branch, use \autoref{thm:separatedmetric-completion-uniqueness-obligation}. These two obligations exhaust the bridge-facing ways to reach the seal.

The carrier contains no Real-completeness, quotient-equality, trichotomy, or representative-selection coordinate. Therefore the seal remains a nonescape boundary for both bridge-facing routes.
\end{proof}

\begin{theorem}[SeparatedMetric bridged-closure readiness]
\label{thm:separatedmetric-bridged-closure-readiness}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Its bridge-facing public surface consists exactly of the $\MetricUp$ distance witness, the $\CompleteMetricUp$ limit rows, the $\CauchySequenceEquivalenceUp$ route, the $\RealUp$ zero seal, the separation classifier row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert$ row. This is the complete surface exported to a bridge consumer.

The surface exports no quotient completion equality, selected limit, host equality, trichotomy, representative-selection row, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with the public identity export of \autoref{thm:separatedmetric-public-identity-export}. It identifies the identity-facing part of the surface as the metric-distance witness, the $\RealUp$ zero seal, the separation classifier, and the support rows $H,C,P,N$.

Next apply the public completion uniqueness export of \autoref{thm:separatedmetric-public-completion-uniqueness-export}. It adds the two $\CompleteMetricUp$ limit rows and the $\CauchySequenceEquivalenceUp$ route, but it does not add a quotient completion equality, selected limit, or host equality row.

Finally use the public Real-seal nonescape export of \autoref{thm:separatedmetric-public-real-seal-nonescape-export}. The Real row remains a zero-distance seal inside the displayed finite certificate route, and the support rows provide only transport, replay, provenance, and local naming. Therefore the listed rows are exactly the bridge-facing readiness surface.
\end{proof}

\begin{theorem}[SeparatedMetric separated-identity transport obligation]
\label{thm:separatedmetric-separated-identity-transport-obligation}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every separated-identity transport read of $S$ is a finite $\BHist$ packet-coordinate route: the $\MetricUp$ distance rows of $X$ expose a distance witness, the $\RealUp$ seal row $D$ reads that witness as zero, $\hsame$ rows in $H$ transport the endpoints and witness, the displayed $\Cont$ replay $C$ preserves the route, and the $\NameCert$ row $N$ names the transported classifier row $Z$.

No such read may bypass $X,D,H,C,P,N$ by parameter transport, host equality, quotient equality, trichotomy, selected representatives, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the packet coordinates from \autoref{def:separatedmetric-carrier}. The identity-facing data are the $\MetricUp$ distance rows in $X$, the $\RealUp$ zero-distance seal $D$, the separation row $Z$, and the structural rows $H,C,P,N$.

Use \autoref{thm:separatedmetric-zero-distance-separation-obligation}. It forces every zero-distance identity read to place the metric-distance witness before the real zero seal and both before the separation classifier.

Transport is then componentwise through $H$ and replayed through $C$. The provenance and local naming rows $P,N$ expose exactly the transported finite route, so the conclusion is classifier equivalence through $Z$ rather than a host-side identity principle.
\end{proof}

\begin{theorem}[SeparatedMetric completion-uniqueness consumer obligation]
\label{thm:separatedmetric-completion-uniqueness-consumer-obligation}
Let $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ carrier. Every completion-uniqueness consumer of $S$ must read the two $\CompleteMetricUp$ limit rows $L_0,L_1$ through the $\CauchySequenceEquivalenceUp$ finite-window route $E$, then through the $\MetricUp$ distance rows of $X$, the $\RealUp$ zero-distance seal $D$, the $\hsame$ transport rows $H$, the displayed $\Cont$ replay $C$, the $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$ before it may consume the classifier row $Z$.

The obligation exports completion-limit uniqueness only as displayed classifier equivalence, not as quotient completion equality, selected host limits, countable choice, host equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Begin with the completion rows $L_0,L_1$. By \autoref{thm:separatedmetric-completion-uniqueness-obligation}, a consumer cannot compare them until the $\CauchySequenceEquivalenceUp$ row $E$ displays the shared regular Cauchy finite windows.

After $E$ is displayed, apply the zero-distance route of \autoref{thm:separatedmetric-zero-distance-separation-obligation}. The comparison must form a metric-distance witness in $X$, read the $\RealUp$ zero seal $D$, and then reach the separation row $Z$.

Finally transport, replay, provenance, and naming pass through $H,C,P,N$. Since no quotient completion object, selected limit, countable-choice schedule, host equality row, or ambient completeness theorem is a packet coordinate, the consumer obligation is exhausted by the displayed rows.
\end{proof}

\begin{theorem}[SeparatedMetric Real-seal zero-distance budget]
\label{thm:separatedmetric-real-seal-zero-distance-budget}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, every $\RealUp$ seal row consumed by a downstream Real-facing or completion-facing read is budgeted to one of two finite routes: a separated-identity route through the $\MetricUp$ distance rows of $X$, $D$, $Z$, $H,C,P,N$, or a completion-uniqueness route through $L_0,L_1,E,X,D,Z,H,C,P,N$ with $E$ displaying the $\CauchySequenceEquivalenceUp$ finite windows.

The budget contains no third route for Real equality, quotient equality, selected representatives, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Use \autoref{thm:separatedmetric-real-seal-nonescape-obligation}. It confines every bridge-facing $\RealUp$ seal read to the separated-metric zero-distance or completion-uniqueness route.

For the identity branch, apply \autoref{thm:separatedmetric-separated-identity-transport-obligation}. The seal is read after the metric-distance witness and before the transported classifier row is named.

For the completion branch, apply \autoref{thm:separatedmetric-completion-uniqueness-consumer-obligation}. The seal is read only after the two $\CompleteMetricUp$ rows and the $\CauchySequenceEquivalenceUp$ finite-window route have been displayed.

The carrier inventory has no coordinate for the excluded third routes. Therefore the Real-seal budget is exactly the two displayed finite routes.
\end{proof}

\begin{theorem}[SeparatedMetric Real zero-distance scope]
\label{thm:separatedmetric-real-zero-distance-scope}
For an accepted $\SeparatedMetricUp$ carrier $S=(X,D,Z,L_0,L_1,E,H,C,P,N)$, every Real-facing zero-distance classifier read must pass through the displayed $\MetricUp$ distance witness in $X$, the $\RealUp$ zero-distance seal $D$, the optional $\CauchySequenceEquivalenceUp$ route $E$ when completion-limit rows $L_0,L_1$ are present, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local $\NameCert$ row $N$ before the separation classifier row $Z$ may be exported.

The export is therefore a local classifier consequence of the displayed zero-distance route. It is not host equality, quotient equality, a selected representative, trichotomy of real comparisons, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the carrier through \autoref{def:separatedmetric-carrier}. The zero-distance branch exposes $X,D,Z,H,C,P,N$, so a Real-facing identity read first forms the $\MetricUp$ distance witness in $X$ and only then reads that witness through the $\RealUp$ seal $D$.

If completion-limit rows are present, apply \autoref{thm:separatedmetric-completion-uniqueness-consumer-obligation}. The read must pass through $L_0,L_1$ and the $\CauchySequenceEquivalenceUp$ row $E$ before it reaches the same metric witness and real zero-distance seal.

Now use the public identity and completion exports, \autoref{thm:separatedmetric-public-identity-export} and \autoref{thm:separatedmetric-public-completion-uniqueness-export}. They place the separated classifier behind the displayed zero-distance and completion-equivalence routes, while \autoref{thm:separatedmetric-public-real-seal-nonescape-export} keeps the $\RealUp$ row inside that route.

Finally transport, replay, provenance, and naming pass through $H,C,P,N$. Since the carrier has no host-equality, quotient-equality, selected-representative, trichotomy, or ambient-completeness coordinate, the classifier export cannot escape the displayed Real zero-distance scope.
\end{proof}

\begin{definition}[SeparatedMetric zero-distance carrier]
\label{def:separated-metric-zero-distance-carrier}
A $\SeparatedMetricUp$ zero-distance carrier is a finite $\BHist$ packet
$$
\mathsf{SepZero}(X,D,Z,E,L,H,C,P,N)
$$
whose coordinates are exactly:
\begin{enumerate}
  \item $X$, the displayed $\MetricUp$ source row containing the carried endpoints and distance witness;
  \item $D$, the $\RealUp$ distance witness row reading that distance as zero;
  \item $Z$, the zero-distance refusal row that permits classifier identification only through the displayed zero-distance route;
  \item $E$, the $\CauchySequenceEquivalenceUp$ handoff row used when the endpoints are completion names;
  \item $L$, the $\CompleteMetricUp$ compatibility row binding completion-limit consumers to the same metric source;
  \item $H$, the componentwise $\hsame$ transport ledger for endpoints, distance witnesses, zero rows, and completion rows;
  \item $C$, the displayed $\Cont$ replay ledger for the same route;
  \item $P$, the $\Pkg$ provenance row naming the source of the carrier;
  \item $N$, the local $\NameCert_{\SeparatedMetricUp}$ row.
\end{enumerate}
The classifier of this carrier compares packets only by these rows. It has no coordinate for host equality, quotient metric equality, selected representatives, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{definition}

\begin{theorem}[SeparatedMetric NameCert obligation surface]
\label{thm:separated-metric-namecert-obligation-surface}
For an accepted $\SeparatedMetricUp$ zero-distance carrier
$$
S=\mathsf{SepZero}(X,D,Z,E,L,H,C,P,N),
$$
the local $\NameCert_{\SeparatedMetricUp}$ surface is exactly the finite obligation surface consisting of the $\MetricUp$ source row $X$, the $\RealUp$ zero-distance witness $D$, the zero-distance refusal row $Z$, the $\CauchySequenceEquivalenceUp$ handoff $E$, the $\CompleteMetricUp$ compatibility row $L$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local naming row $N$.

Every accepted identity or completion-uniqueness read must consume these rows in this order before it may export a point-classifier identification. The surface refuses host equality, quotient equality, selected representatives, trichotomy, open-cover compactness, and ambient completeness data because no such row occurs in $S$.
\end{theorem}
\begin{proof}
Project the coordinates of \autoref{def:separated-metric-zero-distance-carrier}. The first three rows supply the metric source, the real-valued zero-distance witness, and the refusal that prevents classifier identification unless the zero-distance route has been displayed.

For completion-facing reads, use the $\CauchySequenceEquivalenceUp$ and $\CompleteMetricUp$ rows before the separation classifier is consumed. These rows bind completion names to the displayed metric source rather than to a quotient completion object.

Finally transport, replay, provenance, and naming pass through $H,C,P,N$. Since the carrier lists no additional coordinate, every accepted $\NameCert_{\SeparatedMetricUp}$ obligation is exhausted by the stated finite surface.
\end{proof}

\begin{theorem}[SeparatedMetric Cauchy-completion readback]
\label{thm:separated-metric-cauchy-completion-readback}
Let $S=\mathsf{SepZero}(X,D,Z,E,L,H,C,P,N)$ be an accepted $\SeparatedMetricUp$ zero-distance carrier. Any Cauchy or completion consumer that reads a zero-distance collapse from $S$ must route the read through the $\SeparatedMetricUp$ packet together with the displayed $\MetricUp$, $\RealUp$, $\CauchySequenceEquivalenceUp$, and $\CompleteMetricUp$ rows.

The consumer may not read zero-distance collapse from a host Cauchy quotient, an ambient equality of completion endpoints, a selected limit, countable choice, trichotomy, or an untracked completeness theorem. The only exported conclusion is the classifier route named by $N$ after the displayed rows $X,D,Z,E,L,H,C,P$ have been consumed.
\end{theorem}
\begin{proof}
Start with a Cauchy or completion consumer. If it asks for limit identification, the read first passes through $E$ and $L$, so the two completion-facing rows are bound to the same displayed metric source.

Then apply the separated-metric route through $X,D,Z$. The metric row supplies the distance witness, the $\RealUp$ row reads that witness as zero, and the refusal row allows only the corresponding classifier identification.

The remaining rows $H,C,P,N$ transport, replay, source, and name the route. No host quotient, selected limit, countable-choice schedule, trichotomy row, or ambient completeness theorem is present in the carrier, so the readback is confined to the listed BEDC rows.
\end{proof}

\begin{theorem}[SeparatedMetric root completion-limit handoff]
\label{thm:separatedmetric-root-completion-limit-handoff}
Every completion-limit classifier export from an accepted $\SeparatedMetricUp$ zero-distance carrier must first route through the $\CompleteMetricUp$ row, $\CauchySequenceEquivalenceUp$ row, $\MetricUp$ source row, $\RealUp$ zero-distance witness, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ row. The export is therefore a readback of the finite carrier in \autoref{def:separated-metric-zero-distance-carrier} together with \autoref{thm:separated-metric-cauchy-completion-readback}, not a direct read from ambient completion equality.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:separated-metric-zero-distance-carrier}. The completion-facing rows are $L$ and $E$, the metric and zero-distance rows are $X,D,Z$, and the structural rows are $H,C,P,N$.

Use \autoref{thm:separated-metric-cauchy-completion-readback}. It already forces Cauchy and completion consumers to route through the displayed $\SeparatedMetricUp$, $\MetricUp$, $\RealUp$, $\CauchySequenceEquivalenceUp$, and $\CompleteMetricUp$ rows.

The completion-limit classifier export is therefore downstream of $L,E,X,D,Z,H,C,P,N$. Since no host completion equality or selected representative row occurs in the carrier, the export cannot bypass the finite handoff.
\end{proof}

\begin{theorem}[SeparatedMetric root classifier nonescape]
\label{thm:separatedmetric-root-classifier-nonescape}
The separated classifier of an accepted $\SeparatedMetricUp$ zero-distance carrier cannot be consumed from host equality, quotient equality, selected representatives, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness. It is consumable only through the displayed $\MetricUp$ source, $\RealUp$ zero-distance witness, separation row, $\CauchySequenceEquivalenceUp$ handoff, $\CompleteMetricUp$ compatibility row, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and local $\NameCert$ rows.
\end{theorem}
\begin{proof}
Project \autoref{def:separated-metric-zero-distance-carrier}. Its rows are exactly $X,D,Z,E,L,H,C,P,N$, and none of the excluded host or quotient principles is a carrier coordinate.

Apply \autoref{thm:separated-metric-cauchy-completion-readback}. Any completion-facing consumption of the classifier must pass through the displayed Cauchy and completion rows before the local name is exported.

The nonescape claim follows because every permitted classifier read is already accounted for by the finite carrier rows, while host equality, quotient equality, selected representatives, trichotomy, open-cover compactness, and ambient $\RealUp$ completeness have no row to transport, replay, source, or name.
\end{proof}
\input{parts/concrete_instances/separatedmetric/namecert_consumer_coverage}

\input{parts/concrete_instances/separatedmetric/root_obligation_basis}

\begin{closurestatus}{\SeparatedMetricUp}
  \constructivestory{A $\SeparatedMetricUp$ packet is generated from a $\MetricUp$ carrier, a $\RealUp$-valued distance witness, a zero-distance separation row, two $\CompleteMetricUp$ Cauchy-limit rows for one regular Cauchy point name, a $\CauchySequenceEquivalenceUp$ route, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\matureClosure}
  \scopeclosed{\autoref{thm:separatedmetric-bridged-closure-readiness} together with \autoref{thm:separatedmetric-public-identity-export}, \autoref{thm:separatedmetric-public-completion-uniqueness-export}, and \autoref{thm:separatedmetric-public-real-seal-nonescape-export} identifies the mature separated-metric public surface over $\MetricUp$, $\CompleteMetricUp$, $\CauchySequenceEquivalenceUp$, $\RealUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not claim quotient metric spaces, host equality, trichotomy, open-cover compactness, $\RealUp$ completeness, Lean verification, or bridge checking.}
  \upgradepath{No paper-side closure upgrade remains; Lean verification and bridge checking remain separate formal-axis work.}
\end{closurestatus}
