\chapter{A Concrete Naming Certificate for $\BoundedRealSequenceUp$}
\label{ch:concrete-instances-boundedrealsequence-namecert}
\origin{human}

Following Bishop and Bridges, the $\BoundedRealSequenceUp$ packet records a bounded real sequence by finite stream-window rows, regular rational readback, a real-name seal, and a displayed closed-bounded interval net. It sits before the subsequence compactness route of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert} and exposes the boundedness surface that chapter consumes. Its dependency surface is the $\StreamNameUp$ window interface of \autoref{ch:concrete-instances-streamname-namecert}, the $\RegSeqRatUp$ regular-rational readback of \autoref{ch:concrete-instances-regseqrat-namecert}, the terminal $\RealUp$ seal of \autoref{ch:concrete-instances-real-namecert}, and the interval-net bound row of \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}. The packet is a finite certificate for bounded sequence inspection; it is not open-cover compactness, trichotomy of reals, host completeness, quotient equality of streams, or a choice-selected subsequence.

\begin{definition}[Bounded real sequence carrier]
\label{def:bounded-real-sequence-carrier}
A $\BoundedRealSequenceUp$ carrier is a finite $\BHist$ packet
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
with the following displayed rows:
\begin{enumerate}
\item $S$ is the finite source schedule of sequence indices under inspection.
\item $W$ is the finite family of $\StreamNameUp$ windows exposed for the inspected indices in $S$.
\item $Q$ is the $\RegSeqRatUp$ readback row attached to those windows and their dyadic tolerance observations.
\item $R$ is the $\RealUp$ sequence-name seal reached only after $W$ and $Q$ have been displayed.
\item $I$ is the $\ClosedBoundedIntervalNetUp$ bound row carrying the interval net used to witness boundedness for the displayed sequence windows.
\item $H$ stores componentwise $\hsame$ transport for the source schedule, stream windows, regular readback, real seal, interval-net bound, continuation, provenance, and local naming rows.
\item $C$ stores displayed $\Cont$ replay from inspected indices to stream windows, from stream windows to regular readback, from regular readback to the real seal, and from the real seal to the interval-net bound assertion.
\item $P$ is the $\Pkg$ provenance over $\BoundedRealSequenceUp$, $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\ClosedBoundedIntervalNetUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, and $\NameCert$.
\item $N$ is the local $\NameCert_{\BoundedRealSequenceUp}$ row.
\end{enumerate}
The bound row is displayed as the closed interval-net containment surface
$$
\begin{gathered}
I:\ClosedBoundedIntervalNetUp,\\
\forall i\in S_{\mathrm{shown}}\quad W_i\longmapsto Q_i\longmapsto R_i\in I.
\end{gathered}
$$
Here $S_{\mathrm{shown}}$ denotes only the inspected finite index rows of the carrier. The classifier compares accepted packets only through $S,W,Q,R,I,H,C,P,N$ and has no coordinate for trichotomy, host real order completeness, quotient-stream equality, open-cover compactness, or a selected infinite subsequence.
\end{definition}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceTasteGate\_single\_carrier\_alignment}

\begin{theorem}[Bounded real sequence NameCert obligations]
\label{thm:bounded-real-sequence-namecert-obligations}
For every accepted $\BoundedRealSequenceUp$ carrier $B=(S,W,Q,R,I,H,C,P,N)$, the local $\NameCert_{\BoundedRealSequenceUp}$ surface consists exactly of carrier admission for the nine displayed rows, finite source-window coverage through $S$ and $W$, regular rational readback through $Q$, real-name sealing through $R$, closed-bounded interval-net containment through $I$, componentwise $\hsame$ transport through $H$, displayed $\Cont$ replay through $C$, $\Pkg$ provenance through $P$, and local naming through $N$.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.NameCertObligations.BoundedRealSequenceCarrier\_semantic\_name\_certificate}
\begin{proof}
Project the carrier of \autoref{def:bounded-real-sequence-carrier}. The only sequence data available to the classifier are the inspected index schedule $S$, the corresponding $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ readback $Q$, and the downstream $\RealUp$ seal $R$.

Read the bound row next. The $\ClosedBoundedIntervalNetUp$ packet $I$ supplies the finite interval-net containment surface from \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}; boundedness is therefore a displayed row tied to the inspected windows, not an ambient completeness or order-trichotomy principle.

Finally inspect the structural rows. The rows $H,C,P,N$ transport, replay, source, and name only the displayed sequence-window, regular-readback, real-seal, and interval-net rows. Since no other coordinate is present in the carrier, the listed obligations exhaust the local NameCert surface.
\end{proof}

\begin{theorem}[Bounded real sequence finite-window bound]
\label{thm:bounded-real-sequence-finite-window-bound}
Every accepted $\BoundedRealSequenceUp$ carrier preserves boundedness under finite window inspection: any displayed route from an inspected index to a $\RealUp$ sequence-name seal factors through
$$
S\longmapsto W\longmapsto Q\longmapsto R\longmapsto I
$$
together with $H,C,P,N$. Thus a finite-window consumer can read the closed-bounded interval-net bound without importing trichotomy, host completeness, quotient-stream equality, open-cover compactness, or a selected subsequence.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceFiniteWindow\_bound}
\begin{proof}
Begin with an inspected index row in $S$. The continuation row $C$ exposes its $\StreamNameUp$ window in $W$, then the regular rational readback $Q$, and only then the $\RealUp$ seal $R$.

The bound row $I$ is read after this route. It is the finite interval-net containment row supplied by \autoref{ch:concrete-instances-closedboundedintervalnet-namecert}, so the bound is attached to the displayed windows and readbacks rather than to a host-level set of all sequence values.

Transport through $H$ and provenance through $P$ preserve the same route, while $N$ names it locally. Because the carrier has no coordinate for trichotomy, host completeness, quotient equality, open-cover compactness, or selected subsequences, finite-window boundedness cannot leave the displayed path.
\end{proof}

\begin{theorem}[Bounded real sequence Bolzano--Weierstrass handoff]
\label{thm:bounded-real-sequence-bolzano-weierstrass-handoff}
The $\BolzanoWeierstrassUp$ consumer of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert} reads a bounded sequence source from an accepted $\BoundedRealSequenceUp$ carrier only through the finite route
$$
S,W,Q,R,I,H,C,P,N.
$$
Consequently the handoff supplies a reusable bounded real sequence certificate for the L10 real-completion route while leaving open-cover compactness, trichotomy, host completeness, quotient-stream equality, and choice-selected subsequences outside the exported surface.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceBolzanoWeierstrass\_handoff}
\begin{proof}
Use \autoref{thm:bounded-real-sequence-finite-window-bound}. It places every inspected sequence value on the route from $S$ through $W,Q,R$ to the interval-net bound row $I$.

Now read the $\BolzanoWeierstrassUp$ carrier of \autoref{ch:concrete-instances-bolzanoweierstrass-namecert}. Its bounded sequence row is exactly the source surface needed before finite interval nets, regular Cauchy subsequence extraction, RegSeqRat readback, and the Real cluster seal can be consumed.

The structural rows $H,C,P,N$ preserve the finite route across the handoff. Thus the downstream consumer receives a bounded real sequence certificate and receives no additional compactness, trichotomy, host completeness, quotient-stream equality, or arbitrary subsequence selection principle.
\end{proof}

\falsifiablePrediction{Every $\BolzanoWeierstrassUp$ bounded-source read factors through a $\BoundedRealSequenceUp$ route displaying finite stream windows, regular readback, a RealUp seal, and a closed-bounded interval-net row.}

\independenceWitness{streamname, regseqrat, real, closedboundedintervalnet, bolzanoweierstrass: $\BoundedRealSequenceUp$ is not bijective to any listed sibling because it jointly carries a finite sequence schedule, stream windows, regular rational readback, real seals, interval-net boundedness, transport, continuation, provenance, and local naming.}

\begin{theorem}[Bounded real sequence window envelope]
\label{thm:bounded-real-sequence-window-envelope}
Every accepted $\BoundedRealSequenceUp$ carrier exposes a bounded sequence to downstream consumers only through finite $\StreamNameUp$ windows and the displayed $\DyadicRatCoreUp$ bound ledger attached to those windows. In particular, any consumer that reads an inspected index must factor through the visible route
$$
S,W,Q,R,I,H,C,P,N
$$
and cannot extract an infinite stream, quotient sequence equality, host supremum, open-cover compactness proof, or selected subsequence from the carrier.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceWindow\_envelope}
\begin{proof}
Project the carrier of \autoref{def:bounded-real-sequence-carrier}. The inspected source schedule $S$ and finite windows $W$ are the only entry rows for sequence data, so no downstream read starts from an unbounded stream.

The bound is then read through the displayed route to $I$. The regular readback $Q$ and real seal $R$ connect each visible window to the closed-bounded interval-net row, while the dyadic ledger named by the sibling tolerance surface records the finite comparison data needed for the bound.

Rows $H,C,P,N$ transport, replay, source, and name the same route. Since the absent rows are not part of the carrier, the envelope remains a finite-window and finite-ledger surface.
\end{proof}

\begin{theorem}[Bounded real sequence Bolzano--Weierstrass frontier]
\label{thm:bounded-real-sequence-bolzano-frontier}
Any $\BolzanoWeierstrassUp$-facing consumer that receives data from an accepted $\BoundedRealSequenceUp$ carrier receives only the bounded-window frontier
$$
S,W,Q,R,I,H,C,P,N .
$$
The frontier supplies finite bounded real sequence inspection data before the Bolzano--Weierstrass route opens, but it does not provide a selected subsequence, a compactness principle, trichotomy, quotient stream equality, countable choice, or ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceBolzano\_frontier}
\begin{proof}
Use the handoff route of \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}. That theorem identifies the bounded sequence source read by the Bolzano--Weierstrass consumer with the same finite carrier rows.

The frontier is bounded because $I$ is displayed after $S,W,Q,R$. Thus the consumer can inspect finite sequence windows, read them back through $\RegSeqRatUp$, and see the real-seal and interval-net bound rows before any compactness-facing construction is considered.

No selected subsequence or compactness proof is stored in those rows. The frontier therefore hands off bounded-window data only, leaving all choice, quotient, trichotomy, and completeness principles outside the exported surface.
\end{proof}

\begin{theorem}[Bounded real sequence RegSeqRat readback]
\label{thm:bounded-real-sequence-regseqrat-readback}
For every accepted $\BoundedRealSequenceUp$ carrier, each $\RegSeqRatUp$ readback available to a consumer is routed through the same finite bound and real-seal rows:
$$
W\longmapsto Q\longmapsto R\longmapsto I .
$$
Consequently a readback consumer cannot detach the regular rational data from the visible $\StreamNameUp$ window, the $\RealUp$ seal, the $\ClosedBoundedIntervalNetUp$ bound row, or the local structural rows $H,C,P,N$.
\end{theorem}
\begin{proof}
Begin with an exposed window $W_i$ for an inspected index. By the carrier definition, the matching regular rational readback is the corresponding component of $Q$ rather than a host-level sequence object.

The readback continues to the real seal $R_i$ and then to the interval-net bound row $I$. This is the same visible finite bound route used by \autoref{thm:bounded-real-sequence-finite-window-bound}.

The structural rows keep the readback inside the packet. Transport by $H$, replay by $C$, provenance by $P$, and naming by $N$ prevent the regular rational data from escaping as a quotient stream, selected subsequence, compactness witness, or ambient real-completeness datum.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceRegSeqRat\_readback}

\begin{theorem}[Bounded real sequence located-bound handoff]
\label{thm:bounded-real-sequence-located-bound-handoff}
Every accepted $\BoundedRealSequenceUp$ packet whose interval-net row is read as located lower and upper real bounds factors through the $\LocatedBoundedRealSequenceUp$ route of \autoref{ch:concrete-instances-located-bounded-real-sequence-namecert} before any $\BolzanoWeierstrassUp$ consumer inspects it. The visible route is
$$
S,W,Q,R,I \longmapsto \LocatedBoundedRealSequenceUp \longmapsto H,C,P,N .
$$
Thus the closed-bounded interval-net row is narrowed to located lower and upper bound data before the Bolzano--Weierstrass handoff, without exporting compactness, trichotomy, quotient sequence equality, countable choice, or a selected subsequence.
\end{theorem}
\begin{proof}
Project an accepted carrier $B=(S,W,Q,R,I,H,C,P,N)$ from \autoref{def:bounded-real-sequence-carrier}. The sequence source is displayed only through inspected indices $S$, stream windows $W$, regular rational readback $Q$, and the downstream $\RealUp$ seal $R$.

Use \autoref{thm:bounded-real-sequence-finite-window-bound} and \autoref{thm:bounded-real-sequence-regseqrat-readback}. They put every visible sequence value on the route from $W$ through $Q,R$ to the bound row $I$, so the lower and upper endpoint reads of $I$ are tied to the same finite windows.

When $I$ is read as located lower and upper real bounds, the narrower sibling route is exactly the $\LocatedBoundedRealSequenceUp$ packet of \autoref{ch:concrete-instances-located-bounded-real-sequence-namecert}. The structural rows $H,C,P,N$ preserve that route before \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff} lets any $\BolzanoWeierstrassUp$ consumer inspect the bounded source.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.LocatedBoundHandoff.BoundedRealSequenceLocatedBound\_handoff}

\begin{theorem}[Bounded real sequence located-window choice boundary]
\label{thm:bounded-real-sequence-located-window-choice}
Every $\BolzanoWeierstrassUp$ or real-completion consumer reading an accepted $\BoundedRealSequenceUp$ carrier must obtain located lower and upper bound windows through the displayed route
$$
S,W,Q,R,I .
$$
No such consumer may choose a subsequence, ambient bound, quotient sequence, or host completion witness outside the carrier before the stream windows, regular readback, real seal, and interval-net bound row have been displayed.
\end{theorem}
\begin{proof}
Begin with the finite-window bound of \autoref{thm:bounded-real-sequence-finite-window-bound}. It places each inspected sequence value on the route from $S$ through $W,Q,R$ to the interval-net bound row $I$.

Use the RegSeqRat readback and located-bound handoff, \autoref{thm:bounded-real-sequence-regseqrat-readback} and \autoref{thm:bounded-real-sequence-located-bound-handoff}. They tie the located lower and upper endpoint reads of $I$ to the same finite stream windows and regular rational rows.

Finally apply the obligation-closure package of \autoref{thm:bounded-real-sequence-obligation-closure-package}. The package exports only $S,W,Q,R,I,H,C,P,N$, so Bolzano--Weierstrass and real-completion consumers cannot introduce an outside subsequence choice, ambient bound, quotient sequence, or host completion witness.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceLocatedWindowChoice}

\begin{theorem}[Bounded real sequence location induction]
\label{thm:bounded-real-sequence-location-induction}
Let
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
be an accepted $\BoundedRealSequenceUp$ packet whose located-bound row $I$, $\ClosedBoundedIntervalNetUp$ finite-net row, $\StreamNameUp$ windows $W$, $\RegSeqRatUp$ readback $Q$, and $\RealUp$ seal $R$ are displayed. Then every inspected finite prefix admits induction over its window positions: the empty prefix preserves the same located bound row $I$, and each successor read factors through the same route
$$
S,W,Q,R,I,H,C,P,N
$$
so the new visible value remains inside the same located interval and real-seal rows. The induction exports no subsequence selection, real trichotomy, quotient real equality, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Project the accepted carrier $B=(S,W,Q,R,I,H,C,P,N)$. The inspected schedule $S$ and stream windows $W$ are finite, so induction is over the displayed prefix positions rather than over an infinite host stream.

For the empty prefix, read only the already displayed located-bound row $I$. No sequence value has been inspected, and the same $\ClosedBoundedIntervalNetUp$ row remains the active bound.

For the successor step, use \autoref{thm:bounded-real-sequence-finite-window-bound} and \autoref{thm:bounded-real-sequence-regseqrat-readback}. The next window read goes through $W$ to $Q$, then to the $\RealUp$ seal $R$, and then back to the same interval-net row $I$.

The located-bound handoff of \autoref{thm:bounded-real-sequence-located-bound-handoff} keeps the lower and upper endpoint reads attached to this route. Transport, replay, provenance, and naming through $H,C,P,N$ preserve the induction invariant, and the carrier has no coordinate for the excluded subsequence, trichotomy, quotient-equality, or completeness principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_location\_induction}

\begin{theorem}[Bounded real sequence obligation-closure package]
\label{thm:bounded-real-sequence-obligation-closure-package}
For every accepted $\BoundedRealSequenceUp$ carrier, the carrier row of \autoref{def:bounded-real-sequence-carrier}, the NameCert obligation surface of \autoref{thm:bounded-real-sequence-namecert-obligations}, the finite-window bound of \autoref{thm:bounded-real-sequence-finite-window-bound}, the Bolzano--Weierstrass handoff of \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}, the window envelope of \autoref{thm:bounded-real-sequence-window-envelope}, the Bolzano frontier of \autoref{thm:bounded-real-sequence-bolzano-frontier}, the RegSeqRat readback of \autoref{thm:bounded-real-sequence-regseqrat-readback}, and the located-window choice boundary of \autoref{thm:bounded-real-sequence-located-window-choice} assemble the obligationClosure surface over
$$
\StreamNameUp,\quad
\RegSeqRatUp,\quad
\RealUp,\quad
\ClosedBoundedIntervalNetUp,\quad
\DyadicRatCoreUp,\quad
\BHist,\quad
\hsame,\quad
\Cont,\quad
\Pkg,\quad
\NameCert .
$$
The assembled package exports exactly the finite bounded-sequence route $S,W,Q,R,I,H,C,P,N$ and keeps open-cover compactness, trichotomy, host completeness, quotient stream equality, and choice-selected subsequences outside the packet.
\end{theorem}
\begin{proof}
Start with the carrier and NameCert obligations. The carrier definition lists the finite source schedule, stream windows, regular readback, real seal, closed-bounded interval-net row, and the structural rows. The obligation theorem identifies those rows as the complete local certificate surface over $\StreamNameUp$, $\RegSeqRatUp$, $\RealUp$, $\ClosedBoundedIntervalNetUp$, $\DyadicRatCoreUp$, $\BHist$, $\hsame$, $\Cont$, $\Pkg$, and $\NameCert$.

Next use the finite-window bound and handoff theorems. They place every inspected sequence value on the displayed route from $S$ through $W,Q,R$ to $I$, and they show that the $\BolzanoWeierstrassUp$ consumer reads the bounded source only through the same packet.

Finally add the envelope, frontier, and readback rows. These theorems keep downstream reads inside the visible route $S,W,Q,R,I,H,C,P,N$ and prevent the regular rational data from detaching from the bounded-window surface. Since none of the cited rows stores open-cover compactness, trichotomy, host completeness, quotient stream equality, or a choice-selected subsequence, the assembled obligation-closure package exports none of those claims.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.NameCertObligations.BoundedRealSequenceObligation\_closure\_package}

\begin{theorem}[Bounded real sequence carrier admission]
\label{thm:bounded-real-sequence-obligation-carrier-admission}
Every accepted $\BoundedRealSequenceUp$ carrier
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
must expose inspected sequence indices $S$, finite $\StreamNameUp$ windows $W$, $\RegSeqRatUp$ readback $Q$, $\RealUp$ sequence seals $R$, the $\ClosedBoundedIntervalNetUp$ bound row $I$, componentwise transport $H$, displayed replay $C$, package provenance $P$, and the local $\NameCert_{\BoundedRealSequenceUp}$ row $N$ before any $\BolzanoWeierstrassUp$ or real-completion consumer can read the bounded source. The admitted surface exports no open-cover compactness, trichotomy, quotient stream equality, or choice-selected subsequence.
\end{theorem}
\begin{proof}
Project the carrier of \autoref{def:bounded-real-sequence-carrier}. Its displayed tuple is exactly $S,W,Q,R,I,H,C,P,N$, so carrier admission starts with inspected indices, finite windows, regular readback, real sequence seals, the interval-net bound row, and the structural rows.

Use the NameCert obligations of \autoref{thm:bounded-real-sequence-namecert-obligations}. They identify those displayed rows as the complete local certificate surface and prevent a consumer from reading a bounded source before the windows, readback, seal, bound, transport, replay, provenance, and naming rows have appeared.

Apply the finite-window bound and Bolzano--Weierstrass handoff, \autoref{thm:bounded-real-sequence-finite-window-bound} and \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}. The first ties each inspected value to the $\ClosedBoundedIntervalNetUp$ bound row, and the second forces every $\BolzanoWeierstrassUp$ consumer to enter through the same bounded-source route.

Finally use the obligation-closure package of \autoref{thm:bounded-real-sequence-obligation-closure-package}. Since that package contains no open-cover compactness, trichotomy, quotient stream equality, or choice-selected subsequence coordinate, the admitted carrier exports none of those objects to a Bolzano--Weierstrass or real-completion consumer.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceObligation\_carrier\_admission}

\begin{definition}[Bounded real sequence finite-window net]
\label{def:bounded-real-sequence-finite-window-net}
For an accepted $\BoundedRealSequenceUp$ carrier
$$
B=(S,W,Q,R,I,H,C,P,N),
$$
the finite-window net packet is the displayed subroute
$$
\mathcal{N}_B=(S,W,Q,R,I,H,C,P,N)
$$
read as a closed-bounded interval-net source. Its entries are the inspected sequence schedule $S$, the synchronized $\StreamNameUp$ windows $W$, the $\RegSeqRatUp$ readback $Q$, the $\RealUp$ seal row $R$, the $\ClosedBoundedIntervalNetUp$ bound row $I$, componentwise $\hsame$ transport $H$, displayed $\Cont$ replay $C$, $\Pkg$ provenance $P$, and the local $\NameCert_{\BoundedRealSequenceUp}$ row $N$. The packet has no coordinate for an infinite subnet, open-cover compactness, trichotomy, quotient sequence equality, countable choice, or a selected Bolzano--Weierstrass subsequence.
\end{definition}
\leandef{BEDC.Derived.BoundedRealSequenceUp.FiniteWindowNet.BoundedRealSequenceFiniteWindowNet}

\begin{theorem}[Bounded real sequence finite-window net extraction]
\label{thm:bounded-real-sequence-finite-window-net-extraction}
Every accepted $\BoundedRealSequenceUp$ carrier exposes the finite-window net packet of \autoref{def:bounded-real-sequence-finite-window-net} before any $\BolzanoWeierstrassUp$ or real-completion consumer reads the bounded source. In particular, every such consumer factors through
$$
S,W,Q,R,I,H,C,P,N
$$
and receives the closed-bounded interval-net route before it can inspect compactness-facing or completion-facing data.
\end{theorem}
\begin{proof}
Project the accepted carrier and form the packet $\mathcal{N}_B$ from the same rows. The carrier definition supplies $S,W,Q,R,I,H,C,P,N$ in exactly the order needed to read inspected windows, regular readback, real seals, and the interval-net bound row.

Apply \autoref{thm:bounded-real-sequence-finite-window-bound}. It identifies the finite bound route from $S$ through $W,Q,R$ to $I$ and keeps the route outside trichotomy, host completeness, quotient equality, open-cover compactness, and selected subsequences.

Apply \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}. The Bolzano--Weierstrass consumer reads its bounded sequence source only through the same visible rows. The structural rows $H,C,P,N$ then repack transport, replay, provenance, and local naming as the finite-window net packet.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_finite\_window\_net\_extraction}

\begin{theorem}[Bounded real sequence regular-readback stability]
\label{thm:bounded-real-sequence-regular-readback-stability}
Let
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
and
$$
B'=(S',W',Q',R',I',H',C',P',N')
$$
be accepted $\BoundedRealSequenceUp$ carriers. If componentwise $\hsame$ transport identifies the source schedules, stream windows, regular readback rows, real seals, and interval-net bound rows $S,W,Q,R,I$ with $S',W',Q',R',I'$, then the $\RegSeqRatUp$ readback and the closed-bounded interval-net bound row are preserved. Thus the transported packet still exposes the same finite-window net route before any $\BolzanoWeierstrassUp$ or real-completion consumer reads it.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_regular\_readback\_stability}
\begin{proof}
Project both carriers. The hypothesis says that the five analytic rows $S,W,Q,R,I$ and $S',W',Q',R',I'$ agree under the componentwise transport recorded by the $H$ rows.

Use \autoref{thm:bounded-real-sequence-regseqrat-readback}. The readback available to a consumer is attached to the visible route $W\mapsto Q\mapsto R\mapsto I$, so transporting $W,Q,R,I$ preserves the regular rational readback and the bound row together.

Use \autoref{thm:bounded-real-sequence-finite-window-net-extraction} to repack the transported rows as the finite-window net packet. The remaining rows $H,C,P,N$ and $H',C',P',N'$ supply the transport, replay, provenance, and naming data, so no detached compactness, quotient, choice, trichotomy, or completeness coordinate is introduced.
\end{proof}

\begin{theorem}[Bounded real sequence dyadic-bound transport]
\label{thm:bounded-real-sequence-dyadic-bound-transport}
Let
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
be an accepted $\BoundedRealSequenceUp$ carrier. Every boundedness read transported from $B$ to a $\BolzanoWeierstrassUp$ or completion-facing consumer factors through finite stream windows $S,W$, the $\RegSeqRatUp$ readback row $Q$, the $\RealUp$ seal row $R$, the $\ClosedBoundedIntervalNetUp$ bound row $I$, componentwise $\hsame$ transport, displayed $\Cont$ replay, $\Pkg$ provenance, and the local $\NameCert_{\BoundedRealSequenceUp}$ row.

The transported read may carry dyadic lower and upper bound ledgers from the finite window, but it cannot add trichotomy, quotient sequence equality, countable choice, a choice-selected subsequence, open-cover compactness, or ambient real completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_dyadic\_bound\_transport}
\begin{proof}
Project the carrier and read the finite-window net packet of \autoref{def:bounded-real-sequence-finite-window-net}. The packet lists $S,W,Q,R,I,H,C,P,N$ as the complete boundedness route.

Apply \autoref{thm:bounded-real-sequence-regular-readback-stability}. The $\RegSeqRatUp$ readback and interval-net bound row are stable under componentwise transport, so the transported boundedness row remains attached to the same finite stream windows.

Finally use \autoref{thm:bounded-real-sequence-finite-window-net-extraction}. The Bolzano--Weierstrass or completion-facing consumer receives the closed-bounded interval-net source only after $S,W,Q,R,I$ have been displayed, and the structural rows replay the same route without adding any excluded selector or completeness coordinate.
\end{proof}

\begin{theorem}[Bounded real sequence window factorization]
\label{thm:bounded-real-sequence-window-factorization}
For every accepted $\BoundedRealSequenceUp$ carrier, any consumer read of boundedness factors through a finite window prefix before it reaches the $\ClosedBoundedIntervalNetUp$ source. More precisely, the read first inspects the sequence schedule $S$, then the finite $\StreamNameUp$ windows $W$, then the $\RegSeqRatUp$ readback row $Q$, then the $\RealUp$ seal row $R$, and only then the interval-net bound row $I$.

No consumer may bypass this route by asking for an infinite stream object, a quotient sequence equality, countable choice, a selected subsequence, trichotomy, open-cover compactness, or ambient $\RealUp$ completeness.
\end{theorem}
\begin{proof}
Start with an accepted carrier $B=(S,W,Q,R,I,H,C,P,N)$. The carrier makes the inspected schedule and finite stream windows available before any real readback or interval bound can be consumed.

Use \autoref{thm:bounded-real-sequence-finite-window-bound}. It identifies the bound route as a finite passage from $S$ through $W,Q,R$ into the closed-bounded interval-net row $I$.

The structural rows $H,C,P,N$ then transport, replay, source, and name the same finite passage. Since the carrier has no infinite stream, quotient equality, choice, trichotomy, open-cover, selected-subsequence, or ambient-completeness coordinate, the displayed window factorization is exhaustive.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_window\_factorization}

\begin{theorem}[Bounded real sequence window localization]
\label{thm:bounded-real-sequence-window-localization}
Every accepted $\BoundedRealSequenceUp$ packet localizes each inspected finite $\StreamNameUp$ window through the displayed $\ClosedBoundedIntervalNetUp$ row and $\RegSeqRatUp$ readback before any $\BolzanoWeierstrassUp$ consumer may read the bounded source. More precisely, for
$$
B=(S,W,Q,R,I,H,C,P,N)
$$
each inspected window in $W$ is read through
$$
S,W \longmapsto Q \longmapsto R \longmapsto I \longmapsto H,C,P,N .
$$
The localization exports finite window bounds and regular readback only; it exports no host set of all sequence values, no choice-selected subsequence, no quotient stream equality, no open-cover compactness, and no ambient $\RealUp$ completeness.
\end{theorem}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_window\_localization}
\begin{proof}
Project the carrier and use the finite-window net extraction of \autoref{thm:bounded-real-sequence-finite-window-net-extraction}. That result displays $S,W,Q,R,I,H,C,P,N$ as the finite net packet a consumer must read before bounded-source data are available.

Apply regular-readback stability and dyadic-bound transport, \autoref{thm:bounded-real-sequence-regular-readback-stability} and \autoref{thm:bounded-real-sequence-dyadic-bound-transport}. They keep the $\RegSeqRatUp$ row $Q$ attached to the same stream window $W$, real seal $R$, and closed-bounded interval-net row $I$ under componentwise transport.

Finally use the window factorization of \autoref{thm:bounded-real-sequence-window-factorization}. It forces every boundedness read to pass through the inspected finite window before reaching the interval-net row, so a Bolzano--Weierstrass consumer receives only the displayed local route and none of the excluded host-level data.
\end{proof}

\begin{theorem}[Bounded real sequence Bolzano source exactness]
\label{thm:bounded-real-sequence-bolzano-source-exactness}
Every $\BolzanoWeierstrassUp$ source read from an accepted $\BoundedRealSequenceUp$ packet is exactly the finite-window source
$$
S \to W \to Q \to R \to I \to H \to C \to P \to N.
$$
Thus the Bolzano--Weierstrass consumer receives a bounded source only through finite stream windows, regular rational readback, the real-name seal, and the closed-bounded interval-net row; it receives no selected subsequence, no compactness theorem outside the displayed interval-net route, and no ambient real-completeness principle.
\end{theorem}
\begin{proof}
Read the accepted carrier and form the finite-window net packet. The rows $S,W,Q,R,I$ display the source schedule, finite stream names, regular rational readback, real seal, and closed-bounded interval-net bound before the consumer is allowed to read the source.

Apply \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}. That handoff sends Bolzano--Weierstrass consumers to the visible bounded source rather than to a choice-selected subsequence or host compactness theorem.

Use \autoref{thm:bounded-real-sequence-dyadic-bound-transport} to keep the dyadic bound ledger attached to the same source route under transport. The rows $H,C,P,N$ replay, source, and name the handoff, so the source exactness statement has no remaining coordinate for excluded choice, quotient, compactness, trichotomy, or completeness principles.
\end{proof}
\leanchecked{BEDC.Derived.BoundedRealSequenceUp.BoundedRealSequenceCarrier\_bolzano\_source\_exactness}

\closureat{BoundedRealSequenceUp}{seedStr}

\begin{closurestatus}{\BoundedRealSequenceUp}
  \constructivestory{A $\BoundedRealSequenceUp$ packet is generated from inspected sequence indices, finite StreamName windows, RegSeqRat readback, RealUp sequence-name seals, a ClosedBoundedIntervalNet bound row, componentwise transport, displayed continuation replay, package provenance, and a local NameCert row.}
  \theoryclosure{\seedClosure}
  \scopeclosed{\autoref{def:bounded-real-sequence-carrier}, \autoref{thm:bounded-real-sequence-namecert-obligations}, \autoref{thm:bounded-real-sequence-finite-window-bound}, \autoref{thm:bounded-real-sequence-bolzano-weierstrass-handoff}, and \autoref{thm:bounded-real-sequence-located-window-choice} bind the finite-window bounded-sequence source consumed by Bolzano-Weierstrass.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \notclaimed{This chapter does not close Lean verification, bridge checking, open-cover compactness, trichotomy, host completeness, quotient equality of streams, or choice-selected subsequences.}
  \upgradepath{Lean closure requires carrier admission, NameCert obligations, finite-window bound preservation, Bolzano-Weierstrass handoff, and TasteGate field faithfulness for BEDC.Derived.BoundedRealSequenceUp.}
\end{closurestatus}
