\chapter{A Concrete Naming Certificate for $\FoldDefectStokesUp$}
\label{ch:concrete-instances-folddefectstokes-namecert}
\origin{human}

The $\FoldDefectStokesUp$ interface is a BEDC-native finite certificate surface.

The $\FoldDefectStokesUp$ interface names a finite fold-defect ledger whose boundary row accounts for the visible difference between a fold input and its projected fold output. It consumes the fold-source, visible fiber-ledger, and moment-index rows of the $\FoldMomentKernelUp$ carrier in \autoref{ch:concrete-instances-fold-moment-kernel-namecert}, and repackages their endpoint mismatch as its boundary-defect row $B$ and interior ledger $L$. It is a $\mathsf{BHist}$ packet, not an import of external algebra, a chain complex, a topological Stokes theorem, or an ambient quotient calculus. The packet is meant to sit between finite fold consumers such as $\GoldenMeanShiftUp$, $\ZeckendorfNormalUp$, $\AxisAddUp$, and $\FoldMomentKernelUp$ while exporting only displayed rows, routes, provenance, and local $\NameCert$ evidence.

\begin{definition}[FoldDefectStokes carrier]
\label{def:fold-defect-stokes-carrier}
A $\FoldDefectStokesUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
S=(I,O,B,L,H,C,P,N)
$$
with the following visible rows:
\begin{enumerate}
\item $I$ is the fold-input row naming the displayed finite source segment and its local fold order;
\item $O$ is the projected fold-output row read from $I$ through the displayed fold projection;
\item $B$ is the boundary-defect row recording the visible mismatch left at the endpoints of the projection;
\item $L$ is the interior ledger whose entries pair each internal fold step with the local defect contribution that cancels inside the segment;
\item $H$ records componentwise $\hsame$ transports for the input, output, boundary-defect, and interior-ledger rows;
\item $C$ records the $\Cont$ routes by which a consumer reads $I$, then $O$, then the boundary row $B$, and finally the interior ledger $L$;
\item $P$ is the $\Pkg$ provenance naming the finite BEDC packets that own the fold source, projection rule, boundary read, and ledger read;
\item $N$ is the local $\NameCert_{\FoldDefectStokesUp}$ row.
\end{enumerate}
The carrier contains no infinite cochain object, no ambient differential operator, no quotient by invisible cancellations, no host summation law, and no external object.
\end{definition}

\begin{theorem}[FoldDefectStokes NameCert obligations]
\label{thm:fold-defect-stokes-namecert-obligations}
Every accepted $\FoldDefectStokesUp$ packet with carrier \autoref{def:fold-defect-stokes-carrier} carries five local naming-certificate obligations:
\begin{enumerate}
\item carrier habitation by the empty fold input, empty projected output, empty boundary-defect row, and empty interior ledger;
\item classifier laws inherited componentwise from $\hsame$ on the displayed rows $I$, $O$, $B$, $L$, $H$, $C$, $P$, and $N$;
\item projection stability under the displayed $\Cont$ route from fold input $I$ to projected output $O$;
\item boundary-ledger exactness: every internal defect contribution listed in $L$ is paired with a displayed cancellation route, and the unpaired residue is exactly the boundary row $B$;
\item non-escape: every public read of the packet factors through $I$, $O$, $B$, $L$, $H$, $C$, $P$, and $N$ before it can be consumed by another concrete instance.
\end{enumerate}
\end{theorem}
\leanchecked{BEDC.Derived.FoldDefectStokesUp.FoldDefectStokesPacket\_namecert\_obligation\_surface}
\begin{proof}
For habitation, use the empty $\mathsf{BHist}$ row for $I$, $O$, $B$, and $L$. The identity $\hsame$ rows, trivial $\Cont$ routes, empty provenance, and local certificate row repack this as the empty fold-defect carrier.

The classifier laws are componentwise. Reflexivity, symmetry, and transitivity never inspect hidden fold semantics; they compare only the displayed input, output, boundary, ledger, transport, continuation, provenance, and certificate rows.

Projection stability is the stored route from $I$ to $O$. Transporting the input row through $\hsame$ also transports the projected-output row through the corresponding component of $H$.

Boundary-ledger exactness is read from $L$ and $B$. The ledger lists the internal defect contributions together with their displayed cancellation partners, while the boundary row records exactly the remaining endpoint contribution.

The non-escape obligation follows because those rows exhaust the carrier coordinates. A downstream consumer can reach no chain complex, host summation, quotient cancellation, or external calculus datum outside the displayed packet.
\end{proof}

\begin{definition}[FoldDefectStokes empty carrier]
\label{def:fold-defect-stokes-empty-carrier}
The empty $\FoldDefectStokesUp$ carrier is the packet of \autoref{def:fold-defect-stokes-carrier} with empty fold-input row, empty projected-output row, empty boundary-defect row, empty interior ledger, identity componentwise $\hsame$ transports, trivial displayed $\Cont$ routes, empty $\Pkg$ provenance, and the local $\NameCert_{\FoldDefectStokesUp}$ row.
\end{definition}

\begin{theorem}[FoldDefectStokes classifier laws]
\label{thm:fold-defect-stokes-classifier-laws}
For every accepted $\FoldDefectStokesUp$ carrier $S=(I,O,B,L,H,C,P,N)$, the local classifier transported by $H$ is reflexive, symmetric, and transitive on the displayed input, output, boundary, ledger, route, provenance, and naming rows. These laws are componentwise $\hsame$ laws over the carrier of \autoref{def:fold-defect-stokes-carrier} and add no ambient fold equality.
\end{theorem}
\begin{proof}
Use the coordinates of \autoref{def:fold-defect-stokes-carrier}. Reflexivity is obtained by taking the identity $\hsame$ row on each of $I$, $O$, $B$, $L$, $H$, $C$, $P$, and $N$.

Symmetry reverses each displayed transport row. Since the classifier never reads an unrecorded fold operation, reversing the componentwise rows gives the same accepted surface.

Transitivity composes the displayed transports component by component. The boundary-ledger factorization of \autoref{thm:fold-defect-stokes-boundary-ledger} and the finite no-escape boundary of \autoref{thm:fold-defect-stokes-non-escape} ensure that the composed classifier still mentions only the rows of the carrier.
\end{proof}

\begin{theorem}[FoldDefectStokes projection stability]
\label{thm:fold-defect-stokes-projection-stability}
Let $S=(I,O,B,L,H,C,P,N)$ be an accepted $\FoldDefectStokesUp$ carrier. Any accepted transport of the fold-input row $I$ through the displayed classifier keeps the projected-output row $O$ readable through the same $I$-to-$O$ $\Cont$ route, with the transported boundary row $B$ and ledger row $L$ still factoring as in \autoref{thm:fold-defect-stokes-boundary-ledger}.
\end{theorem}
\leanchecked{BEDC.Derived.FoldDefectStokesUp.FoldDefectStokesPacket\_projection\_stability}
\begin{proof}
Start from the $I$-to-$O$ route stored in $C$. Transporting $I$ by the displayed classifier also transports the corresponding output coordinate through the matching component of $H$.

The boundary and ledger coordinates are then read through the same continuation route. Apply \autoref{thm:fold-defect-stokes-boundary-ledger} to identify the transported public defect with the boundary row and the interior ledger.

Finally, \autoref{thm:fold-defect-stokes-non-escape} rules out any alternate output route through an external fold semantics, quotient, or host summation law.
\end{proof}

\begin{theorem}[FoldDefectStokes exactness obligation]
\label{thm:fold-defect-stokes-exactness-obligation}
For every accepted $\FoldDefectStokesUp$ carrier $S=(I,O,B,L,H,C,P,N)$, the ledger $L$ is exact at the public boundary row $B$: each internal defect contribution recorded in $L$ is paired with a displayed cancellation route, and the remaining public defect is precisely the boundary read $B$ certified by \autoref{thm:fold-defect-stokes-boundary-ledger}.
\end{theorem}
\begin{proof}
Inspect the ledger coordinate in \autoref{def:fold-defect-stokes-carrier}. Its entries are internal defect rows together with the displayed cancellation data that removes them from the endpoint read.

Apply \autoref{thm:fold-defect-stokes-boundary-ledger}. The theorem says every public defect factors through $B$ and $L$, so the only contributions not canceled inside $L$ are exactly the entries represented by the boundary row.

The non-escape boundary of \autoref{thm:fold-defect-stokes-non-escape} keeps the obligation local: there is no hidden differential, quotient cancellation, or host telescoping sum that could change the boundary after the ledger is read.
\end{proof}

\begin{theorem}[FoldDefectStokes boundary-ledger factorization]
\label{thm:fold-defect-stokes-boundary-ledger}
Let $S=(I,O,B,L,H,C,P,N)$ be an accepted $\FoldDefectStokesUp$ carrier. Any public defect read from the projected fold output factors through the displayed route
$$
I \xrightarrow{C} O \xrightarrow{C} B \xleftarrow{C} L
$$
together with the componentwise transport row $H$, package provenance $P$, and local certificate row $N$. In particular, an interior contribution affects the public boundary only by appearing in $L$ with its displayed cancellation partner or by being recorded as part of the boundary row $B$.
\end{theorem}
\leanchecked{BEDC.Derived.FoldDefectStokesUp.FoldDefectStokesPacket\_boundary\_ledger}
\begin{proof}
Start with a public request for a fold-defect read. The carrier first exposes the fold input row $I$ and the projected fold-output row $O$ through the stored continuation route.

The same route then reaches the boundary row $B$. No consumer can read a defect value before passing through the boundary row, because the carrier has no separate defect coordinate.

It remains to account for the interior ledger. Each internal contribution is listed in $L$ together with the displayed cancellation route that removes it from the endpoint read. Contributions without such an internal cancellation are precisely the entries represented by $B$.

Transport row $H$, provenance $P$, and certificate row $N$ make this factorization stable under accepted row movement. Thus the public defect read is a boundary-ledger read over the finite carrier and not an appeal to host algebra.
\end{proof}

\begin{theorem}[FoldDefectStokes non-escape boundary]
\label{thm:fold-defect-stokes-non-escape}
The $\FoldDefectStokesUp$ public boundary exports only the fold-input row, projected fold-output row, boundary-defect row, interior cancellation ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and local $\NameCert$ evidence. It exports no external import, no infinite complex, no ambient differential, no quotient of defects, no host telescoping sum, and no standard Stokes bridge.
\end{theorem}
\leanchecked{BEDC.Derived.FoldDefectStokesUp.FoldDefectStokesPacket\_non\_escape\_boundary}
\begin{proof}
Inspect the carrier coordinates of \autoref{def:fold-defect-stokes-carrier}. The only exported rows are $I$, $O$, $B$, $L$, $H$, $C$, $P$, and $N$.

By \autoref{thm:fold-defect-stokes-boundary-ledger}, every public defect read factors through the boundary and ledger rows. The factorization has no coordinate for an external differential, quotient, infinite object, or host summation operation.

Therefore the public boundary can feed finite BEDC consumers that already understand fold inputs, boundary rows, and ledgers, but it cannot export any stronger calculus or bridge statement.
\end{proof}

\closureat{FoldDefectStokesUp}{seedStr}

\begin{closurestatus}{\FoldDefectStokesUp}
  \constructivestory{A $\FoldDefectStokesUp$ packet is generated from a finite fold-input row, projected fold-output row, boundary-defect row, interior cancellation ledger, componentwise $\hsame$ transports, displayed $\Cont$ routes, package provenance, and local $\NameCert$ evidence.}
  \theoryclosure{\seedClosure}
  \scopeclosed{The seed scope registers the finite carrier, five NameCert obligations, boundary-ledger factorization, and no-escape boundary for fold-defect packets.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not close external imports, infinite complexes, ambient differentials, quotient defect algebra, host telescoping sums, standard Stokes bridges, or bridge checking.}
  \upgradepath{Obligation closure requires Lean targets for carrier habitation, classifier laws, projection stability, boundary-ledger exactness, and the finite no-escape boundary under \texttt{BEDC.Derived.FoldDefectStokesUp}.}
\end{closurestatus}
