\chapter{A Concrete Naming Certificate for $\ContractionMappingUp$}
\label{ch:concrete-instances-contractionmapping-namecert}
\origin{human}

Following Banach's contraction principle and Bishop--Bridges constructive analysis, a $\ContractionMappingUp$ packet defines a contraction mapping as a certified self-map of a metric carrier with a displayed rational bound below one, not as a selected fixed point. The packet is the map-level interface consumed by the fixed-point route: it refines the Lipschitz carrier of \autoref{ch:concrete-instances-lipschitzmap-namecert}, reads its domain through \autoref{ch:concrete-instances-metric-namecert}, hands finite iterate estimates to \autoref{ch:concrete-instances-picardcontraction-namecert}, routes complete-metric consumers through \autoref{ch:concrete-instances-completemetric-namecert}, and supplies the contraction row that \autoref{ch:concrete-instances-banach-fixed-point-namecert} uses before any endpoint seal is read.

\begin{definition}[ContractionMapping carrier]
\label{def:contraction-mapping-carrier}
A $\ContractionMappingUp$ carrier is a finite $\mathsf{BHist}$ packet
$$
K=(X,d,T,G,\lambda,M,I,H,C,P,N)
$$
with the following visible coordinates:
\begin{enumerate}
\item $X$ is the carried $\MetricUp$ point-carrier row;
\item $d$ is the metric-distance witness row used to read source and target distances inside the same carrier;
\item $T$ is the self-map code row, displaying the route from a carried point history of $X$ to another carried point history of $X$;
\item $G$ is the graph row witnessing that each accepted application of $T$ is a finite BEDC graph read rather than a host function application;
\item $\lambda$ is the rational contraction-bound ledger, with displayed nonnegativity and strict unit-bound rows;
\item $M$ is the induced modulus row obtained from the displayed bound ledger and the metric-distance reads;
\item $I$ is the one-step $\PicardContractionUp$ route recording $x\mapsto T(x)$ and the contracted distance comparison for adjacent iterate reads;
\item $H$ stores componentwise $\hsame$ transports for the metric carrier, distance row, self-map row, graph row, rational bound, induced modulus, Picard route, continuation rows, provenance row, and local naming row;
\item $C$ stores the $\Cont$ routes for metric reads, self-map application, graph replay, bound comparison, induced-modulus readback, Picard-step replay, and consumer handoff;
\item $P$ is the $\Pkg$ provenance row over $\MetricUp$, $\LipschitzMapUp$, $\PicardContractionUp$, $\CompleteMetricUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, and $\NameCert$ dependency rows;
\item $N$ is the local $\NameCert_{\ContractionMappingUp}$ row.
\end{enumerate}
The carrier exposes a self-map contraction surface. It contains no coordinate for a selected fixed point, ambient completeness, quotient map equality, host function extensionality, or bridge checking.
\end{definition}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingTasteGate\_single\_carrier\_alignment}
\leandef{BEDC.Derived.ContractionMappingUp.ContractionMappingUp}

\begin{theorem}[ContractionMapping NameCert obligations]
\label{thm:contraction-mapping-namecert-obligations}
For an accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$, the local $\NameCert_{\ContractionMappingUp}$ surface consists of carrier admission, componentwise classifier transport, self-map graph exactness, rational bound stability below one, induced modulus visibility, one-step Picard route compatibility, package provenance stability, and local naming for the finite packet of \autoref{def:contraction-mapping-carrier}.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.TasteGate.ContractionMappingTasteGate\_single\_carrier\_alignment}
\begin{proof}
Carrier admission is exactly the displayed tuple of metric, distance, self-map, graph, bound, modulus, Picard-route, transport, continuation, provenance, and naming rows.

Classifier transport is componentwise. The $\hsame$ rows move the carrier, distance, self-map, graph, bound, modulus, Picard, provenance, and naming data, while the $\Cont$ rows replay metric reads, application, graph inspection, bound comparison, and Picard-step handoff.

Exactness and stability are field exclusions plus the displayed bound ledger. Every accepted target-distance read factors through $d$, $T$, $G$, and $\lambda$, and $\lambda$ carries the strict unit-bound row needed by contraction consumers.

The package and local certificate rows list only the stated dependencies. Repacking these visible rows gives the local naming surface without selecting a fixed point, asserting completeness, quotienting maps, or invoking a bridge.
\end{proof}

\begin{theorem}[ContractionMapping Picard-step contraction]
\label{thm:contraction-mapping-picard-step-contraction}
Every accepted $\ContractionMappingUp$ carrier exposes a finite $\PicardContractionUp$ one-step route $I$. For any displayed adjacent source histories $x,y$ in the carried metric row, the graph reads for $T(x)$ and $T(y)$ and the rational ledger $\lambda$ give the finite comparison
$$
d(T(x),T(y))\leq \lambda\, d(x,y),
$$
with the strict unit-bound row of $\lambda$ retained as part of the packet.
\end{theorem}
\begin{proof}
Read the self-map coordinate $T$ and graph coordinate $G$. They provide finite application rows for $x\mapsto T(x)$ and $y\mapsto T(y)$ inside the same metric carrier $X$.

The distance row $d$ reads both the source distance and the target distance. The rational ledger $\lambda$ is stored with the displayed comparison row and the strict unit-bound row, so the target-distance comparison is a packet field rather than a host analytic inference.

The one-step Picard route $I$ records exactly this application-and-comparison pattern. Since $I$ has no infinite-orbit coordinate, the theorem exports only the adjacent-step contraction surface consumed by $\PicardContractionUp$.
\end{proof}

\begin{definition}[ContractionMapping Cauchy orbit ledger]
\label{def:contraction-mapping-cauchy-orbit-ledger}
For an accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$, a finite Cauchy-orbit ledger is a displayed packet
$$
O=(x_0,\ell,B,R,W)
$$
where $x_0$ is the starting point row in $X$, $\ell$ is a finite $\ListUp$ of Picard iterates $x_0,T(x_0),\ldots,T^n(x_0)$ read through $G$, $B$ is the rational bound-power row storing the inspected powers of $\lambda$, $R$ is the dyadic tolerance row used for adjacent and tail comparisons, and $W$ is the displayed distance-contraction route
$$
d(x_{i+1},x_{i+2})\leq \lambda\,d(x_i,x_{i+1})
\quad\text{and}\quad
d(x_i,x_j)\leq B(i,j)\,d(x_0,x_1)
$$
for the finite indices carried by $\ell$ and $R$.
The ledger contains no selected limit point, no completed orbit, no ambient completeness row, and no host fixed-point equality.
\end{definition}

\begin{theorem}[ContractionMapping Cauchy-orbit contractivity]
\label{thm:contraction-mapping-cauchy-orbit-contractivity}
For every accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$ and every finite Cauchy-orbit ledger $O=(x_0,\ell,B,R,W)$ of \autoref{def:contraction-mapping-cauchy-orbit-ledger}, each adjacent iterate comparison in $\ell$ factors through the stored $\MetricUp$ carrier row $X,d$, the graph row $G$, the rational bound ledger $\lambda$, and the $\PicardContractionUp$ route $I$. The dyadic tolerance row $R$ and bound-power row $B$ only replay those finite comparisons; they do not introduce a separate convergence theorem.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_cauchy\_orbit\_contractivity}
\begin{proof}
Project the contraction carrier. The metric carrier and distance row $X,d$ are the only source of distance comparisons, and the self-map is available only through $T$ and the graph row $G$.

Use \autoref{thm:contraction-mapping-picard-step-contraction} at each displayed adjacent pair in the finite list $\ell$. The theorem supplies the comparison through $G$, $\lambda$, and the Picard route $I$ for that pair.

The ledger rows $B,R,W$ then record only finite replay data: bound powers, dyadic tolerances, and the displayed chain of inequalities already obtained from the adjacent-step route. Since no row of $O$ carries a limit or an ambient completeness witness, the contractivity statement remains a finite orbit ledger.
\end{proof}

\begin{theorem}[ContractionMapping Banach handoff]
\label{thm:contraction-mapping-banach-handoff}
Every $\BanachFixedPointUp$ consumer of an accepted $\ContractionMappingUp$ carrier receives the finite Cauchy-orbit ledger of \autoref{def:contraction-mapping-cauchy-orbit-ledger} together with a separate $\CompleteMetricUp$ row. The handoff exports the displayed Picard iterates, dyadic tolerances, rational bound powers, graph reads, and finite Cauchy comparison route; it does not export a selected fixed point, a completed orbit endpoint, host fixed-point equality, quotient equality of maps, or ambient completeness from the contraction packet alone.
\end{theorem}
\begin{proof}
Begin with the complete-metric handoff of \autoref{thm:contraction-mapping-complete-metric-handoff}. It makes the metric carrier, graph-exact self-map, rational contraction ledger, induced modulus, and Picard one-step route visible, but it explicitly does not supply completeness as a contraction-packet coordinate.

Attach the finite orbit ledger $O$. By \autoref{thm:contraction-mapping-cauchy-orbit-contractivity}, every adjacent and tail comparison in $O$ is replayed through $X,d,G,\lambda,I$ and the ledger rows $B,R,W$.

A $\BanachFixedPointUp$ consumer must therefore add the separate $\CompleteMetricUp$ row before any endpoint seal can be read. The contraction packet and orbit ledger give only finite Cauchy evidence; fixed-point selection, completed endpoints, host equality, quotient map equality, and ambient completeness remain outside the handoff.
\end{proof}

\begin{theorem}[ContractionMapping complete-metric handoff]
\label{thm:contraction-mapping-complete-metric-handoff}
Every $\CompleteMetricUp$ or $\BanachFixedPointUp$ consumer of an accepted $\ContractionMappingUp$ carrier must pass through the rows
$$
X,\ d,\ T,\ G,\ \lambda,\ M,\ I,\ H,\ C,\ P,\ N.
$$
The handoff provides a metric self-map, a graph-exact contraction comparison, an induced modulus, and the one-step Picard route. It does not provide a complete carrier by itself, a Cauchy-limit endpoint, host fixed-point equality, quotient equality of maps, or bridge-checked standardization.
\end{theorem}
\begin{proof}
The carrier inventory in \autoref{def:contraction-mapping-carrier} lists all rows available to a consumer. A complete-metric consumer may read the metric row $X,d$, the self-map and graph rows $T,G$, the rational contraction ledger $\lambda$, and the induced modulus $M$.

The Picard-facing part is supplied by \autoref{thm:contraction-mapping-picard-step-contraction}: it is the finite one-step route $I$, transported by $H$ and replayed by $C$.

Completeness is not a coordinate of the contraction packet. A $\CompleteMetricUp$ handoff therefore requires a separate complete-metric row, and a $\BanachFixedPointUp$ endpoint route requires the later Picard, modulus, completion, and seal rows named in its own carrier. The contraction packet contributes only the map-level surface displayed here.
\end{proof}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_complete\_metric\_handoff}

\begin{theorem}[ContractionMapping tail-modulus readiness]
\label{thm:contraction-mapping-tail-modulus-readiness}
For every accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$ and every finite Cauchy-orbit ledger $O=(x_0,\ell,B,R,W)$, the finite orbit ledger together with the rational contraction bound yields a displayed tail-modulus row for Picard iterates through $\MetricUp$, $\LipschitzMapUp$, $\PicardContractionUp$, and $\CompleteMetricUp$. The row is read from the metric carrier and distance surface $X,d$, the graph-exact self-map $T,G$, the strict unit-bound ledger $\lambda$, the induced modulus $M$, the Picard route $I$, and the finite replay rows $B,R,W$; it does not select a limit point.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_tail\_modulus\_readiness}
\begin{proof}
Project the carrier of \autoref{def:contraction-mapping-carrier}. The metric and distance rows $X,d$ provide the only distance reads, while $T,G$ provide graph-exact applications of the self-map.

Use \autoref{thm:contraction-mapping-picard-step-contraction} for adjacent Picard comparisons and \autoref{thm:contraction-mapping-cauchy-orbit-contractivity} for their finite replay through the orbit ledger. The rational bound ledger $\lambda$ and induced modulus row $M$ are therefore visible before any tail claim is made.

The Banach and complete-metric handoffs, \autoref{thm:contraction-mapping-banach-handoff} and \autoref{thm:contraction-mapping-complete-metric-handoff}, identify the consumer route. They require a separate $\CompleteMetricUp$ row and preserve the same finite $\MetricUp$, $\LipschitzMapUp$, and $\PicardContractionUp$ reads, so the exported tail-modulus row is readiness data rather than a selected endpoint.
\end{proof}

\begin{definition}[ContractionMapping regular-Cauchy modulus surface]
\label{def:contraction-mapping-regular-cauchy-modulus-surface}
For an accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$ and a finite Cauchy-orbit ledger $O=(x_0,\ell,B,R,W)$, the regular-Cauchy modulus surface is the displayed packet
$$
\Theta=(X,d,T,G,\lambda,M,I,O,Q,H,C,P,N)
$$
where $Q$ records the finite tail-bound thresholds extracted from $B,R,W$ and presents them to a $\RegSeqRatUp$-facing consumer. The surface is a route from contraction data to regular-Cauchy completion evidence. It is not a fixed-point selector, not a completed endpoint, not quotient equality of Picard streams, and not ambient completeness.
\end{definition}

\begin{theorem}[ContractionMapping tail-bound extraction]
\label{thm:contraction-mapping-tail-bound-extraction}
For every accepted $\ContractionMappingUp$ carrier $K$ and finite Cauchy-orbit ledger $O$, the tail-modulus readiness row of \autoref{thm:contraction-mapping-tail-modulus-readiness} determines a finite extraction row $Q$ whose entries are read only from the Picard-step contraction route, the Cauchy-orbit contractivity ledger, the rational bound powers, and the dyadic tail tolerance rows. No extraction step reads a selected fixed point or a completed limit.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_tail\_bound\_extraction}
\begin{proof}
Project the carrier and the orbit ledger. The only contraction comparison is the Picard-step route of \autoref{thm:contraction-mapping-picard-step-contraction}, and the only iterated replay is the Cauchy-orbit contractivity statement of \autoref{thm:contraction-mapping-cauchy-orbit-contractivity}.

The finite bound-power row $B$ and tolerance row $R$ provide the threshold entries used by $Q$. The readiness theorem then identifies those entries as the tail-modulus row visible to completion consumers.

Because the complete-metric handoff is still separate, the extraction has no coordinate for an endpoint, selected fixed point, host fixed-point equality, quotient stream equality, or ambient completeness.
\end{proof}

\begin{theorem}[ContractionMapping regular-Cauchy modulus export]
\label{thm:contraction-mapping-regular-cauchy-modulus-export}
Every $\RegSeqRatUp$-facing completion consumer of a $\ContractionMappingUp$ packet may read the surface of \autoref{def:contraction-mapping-regular-cauchy-modulus-surface} only through the finite route
$$
X,d,T,G,\lambda,M,I,O,Q,H,C,P,N.
$$
The route exports a regular-Cauchy modulus for the Picard orbit by combining the stored contraction comparison, finite orbit ledger, tail-bound extraction row, and replay data; it does not export a selected fixed point.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_regular\_cauchy\_modulus\_export}
\begin{proof}
Begin with the tail-bound extraction theorem. It supplies $Q$ from the already displayed contraction route and finite orbit ledger.

Next use \autoref{def:contraction-mapping-regular-cauchy-modulus-surface}. The surface appends $Q$ to the carrier and orbit rows, so a regular-Cauchy consumer sees exactly the metric, self-map, graph, bound, Picard, orbit, threshold, transport, replay, provenance, and local naming rows.

The Banach handoff remains downstream. Thus the exported data is a modulus surface for a regular-Cauchy Picard name, not a fixed-point endpoint, completed orbit, quotient equality, host function equality, or completeness assertion.
\end{proof}

\begin{theorem}[ContractionMapping complete-metric regular-Cauchy handoff]
\label{thm:contraction-mapping-complete-metric-regular-cauchy-handoff}
Every $\CompleteMetricUp$ or $\BanachFixedPointUp$ consumer that uses a $\ContractionMappingUp$ carrier for completion evidence must first read the regular-Cauchy modulus export of \autoref{thm:contraction-mapping-regular-cauchy-modulus-export} and then supply its separate complete-metric row. The contraction packet contributes only the finite RegSeqRat-facing modulus route for the Picard orbit.
\end{theorem}
\begin{proof}
Apply \autoref{thm:contraction-mapping-complete-metric-handoff}. It keeps completeness outside the contraction packet while exposing the metric self-map, contraction comparison, induced modulus, and Picard route.

Apply \autoref{thm:contraction-mapping-regular-cauchy-modulus-export}. It repacks the finite orbit ledger and extracted tail-bound row as the RegSeqRat-facing modulus surface needed by a completion consumer.

Only after those rows are displayed can a $\CompleteMetricUp$ or $\BanachFixedPointUp$ packet use its own endpoint discipline. The contraction packet itself therefore exports regular-Cauchy completion evidence, not endpoint selection, host fixed-point equality, quotient map equality, or ambient completeness.
\end{proof}

\begin{theorem}[ContractionMapping fixed-point readiness]
\label{thm:contraction-mapping-fixed-point-readiness}
Every $\BanachFixedPointUp$ consumer may read an accepted $\ContractionMappingUp$ packet only after the complete-metric row of \autoref{thm:contraction-mapping-complete-metric-handoff} and the finite tail-modulus route of \autoref{thm:contraction-mapping-tail-modulus-readiness} have both been displayed. This readiness condition exposes the contraction packet, Picard iterates, finite Cauchy ledger, rational bound powers, and complete-metric handoff, but it does not select a fixed point, a completed orbit endpoint, or a host equality proof.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_fixed\_point\_readiness}
\begin{proof}
Start with a $\BanachFixedPointUp$ consumer. By \autoref{thm:contraction-mapping-banach-handoff}, it receives the finite Cauchy-orbit ledger and a separate $\CompleteMetricUp$ row rather than an endpoint from the contraction packet alone.

The complete-metric handoff of \autoref{thm:contraction-mapping-complete-metric-handoff} makes the metric self-map, graph-exact contraction comparison, induced modulus, and one-step Picard route visible. The tail-modulus readiness theorem then packages the finite Picard comparisons into the displayed tail route required by the consumer.

Only after both rows are displayed may the consumer proceed to its own fixed-point seal. Because neither row contains a selected point, completed orbit endpoint, host fixed-point equality, quotient map equality, or ambient completeness coordinate, the readiness statement remains a finite obligation boundary.
\end{proof}

\begin{theorem}[ContractionMapping orbit uniqueness window]
\label{thm:contraction-mapping-orbit-uniqueness-window}
Let $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$ be an accepted $\ContractionMappingUp$ carrier, and let
$$
O=(x_0,\ell,B,R,W)
\quad\text{and}\quad
O'=(x'_0,\ell',B',R',W')
$$
be finite Cauchy-orbit ledgers for the same packet. If $x_0$ and $x'_0$ are classifier-stable as the same starting row and both ledgers replay the same graph-exact self-map row $T,G$, then every common finite window of $\ell$ and $\ell'$ is classifier-stable through the stored $\MetricUp$, $\LipschitzMapUp$, and $\PicardContractionUp$ rows. The comparison uses only $X,d,G,\lambda,M,I,H,C$ and the finite ledger rows; it does not assert an infinite orbit or a selected endpoint.
\end{theorem}
\begin{proof}
Project the two orbit ledgers and the accepted contraction carrier. The hypotheses identify the starting rows through the local classifier and require both lists to replay the same self-map graph row $G$.

Induct over the common finite window. The base row is the shared start. At the successor step, graph exactness for $T,G$ gives the next iterate in both ledgers, while the $\MetricUp$ distance row $d$ and the $\LipschitzMapUp$ contraction ledger $\lambda$ keep the comparison inside the same metric carrier.

The $\PicardContractionUp$ route $I$ is the stored one-step replay for each adjacent pair. Transport by $H$ and continuation by $C$ preserve those rows componentwise, so the two finite windows remain classifier-stable without producing any completed orbit or fixed-point endpoint.
\end{proof}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_orbit\_uniqueness\_window}

\begin{theorem}[ContractionMapping fixed-point tail seal]
\label{thm:contraction-mapping-fixed-point-tail-seal}
Before a $\BanachFixedPointUp$ consumer supplies the separate $\CompleteMetricUp$ row, the only endpoint-facing seal exported by an accepted $\ContractionMappingUp$ packet is the finite tail-modulus route of \autoref{thm:contraction-mapping-tail-modulus-readiness}. Thus every fixed-point-facing request must pass through the graph-exact self-map $T,G$, rational bound ledger $\lambda$, induced modulus $M$, Picard route $I$, finite orbit ledger $O$, and complete-metric handoff boundary; the contraction packet alone cannot select a fixed point or certify a completed endpoint.
\end{theorem}
\begin{proof}
Begin with fixed-point readiness in \autoref{thm:contraction-mapping-fixed-point-readiness}. It requires both the complete-metric handoff and the finite tail-modulus route before a Banach consumer may proceed.

Use the tail-modulus readiness theorem. The route it exports is read from $X,d,T,G,\lambda,M,I$ and the finite ledger rows $B,R,W$, so it is endpoint-facing only as a tail seal over finite Picard data.

The complete-metric row is deliberately outside the contraction packet. Consequently no row of $K$ can supply a selected fixed point, completed orbit endpoint, host fixed-point equality, quotient map equality, or ambient completeness proof before the downstream Banach chapter consumes its own complete-metric data.
\end{proof}

\begin{theorem}[ContractionMapping complete-metric consumer package]
\label{thm:contraction-mapping-complete-metric-consumer-package}
For every accepted $\ContractionMappingUp$ carrier $K=(X,d,T,G,\lambda,M,I,H,C,P,N)$ and finite Cauchy-orbit ledger $O=(x_0,\ell,B,R,W)$, the local NameCert obligation surface needed by downstream Banach, Picard, complete-metric, and Lipschitz consumers is the package consisting of the complete-metric handoff of \autoref{thm:contraction-mapping-complete-metric-handoff}, the tail-modulus readiness route of \autoref{thm:contraction-mapping-tail-modulus-readiness}, the fixed-point readiness boundary of \autoref{thm:contraction-mapping-fixed-point-readiness}, and the orbit uniqueness window of \autoref{thm:contraction-mapping-orbit-uniqueness-window}. This package remains finite and $\BHist$-anchored and does not claim a selected fixed point.
\end{theorem}
\begin{proof}
Read the complete-metric handoff first. It exposes the metric carrier, graph-exact self-map, rational contraction ledger, induced modulus, and Picard one-step route while leaving the actual complete-metric row to the consumer.

Next attach the finite orbit data. Tail-modulus readiness supplies the tail route through the ledger rows, and the orbit uniqueness window makes matching finite Picard windows stable under the same classifier and graph replay.

Finally use fixed-point readiness to delimit the downstream obligation. The package now contains exactly the finite rows that Banach, Picard, complete-metric, and Lipschitz consumers need to read before their own endpoint arguments begin, with no coordinate for endpoint selection, completed orbit equality, or host fixed-point proof.
\end{proof}

\begin{definition}[ContractionMapping scoped source stack]
\label{def:contraction-mapping-scoped-source-stack}
The scoped source stack for a $\ContractionMappingUp$ read is the finite packet
$$
\mathcal S_{\ContractionMappingUp}
=(\MetricUp,\LipschitzMapUp,\PicardContractionUp,\CompleteMetricUp,\RegSeqRatUp,\mathsf{BHist},\hsame,\Cont,\mathsf{Pkg},\NameCert).
$$
It is read through the carrier rows $X,d,T,G,\lambda,M,I,H,C,P,N$ and the orbit and modulus rows $O,Q$ displayed in this chapter. The stack records source metric data, Lipschitz and contraction graph data, Picard-step replay, completion-facing modulus handoff, regular-rational tail thresholds, history transport, continuation replay, provenance, and local naming; it contains no fixed-point selector or completed endpoint.
\end{definition}

\begin{theorem}[ContractionMapping scoped dependency surface]
\label{thm:contraction-mapping-scoped-dependency-surface}
Every accepted $\ContractionMappingUp$ read factors through the scoped source stack of \autoref{def:contraction-mapping-scoped-source-stack}. In particular, any Picard, Banach, complete-metric, or regular-Cauchy consumer can inspect only the displayed $\MetricUp$, $\LipschitzMapUp$, $\PicardContractionUp$, $\CompleteMetricUp$, $\RegSeqRatUp$, $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ rows before it uses its own downstream endpoint discipline.
\end{theorem}
\leanchecked{BEDC.Derived.ContractionMappingUp.ContractionMappingCarrier\_scoped\_dependency\_surface}
\begin{proof}
Project the carrier and the finite orbit rows. The carrier supplies the metric, graph, contraction bound, induced modulus, Picard route, transport, replay, provenance, and naming coordinates, while the orbit and threshold rows supply only finite Picard tail data.

Apply the complete-metric and Banach handoffs. They expose a separate $\CompleteMetricUp$ row for completion-facing consumers and keep endpoint selection outside the contraction packet.

Apply the regular-Cauchy export and complete-metric regular-Cauchy handoff. They place the tail thresholds in the $\RegSeqRatUp$-facing part of the stack, transported by the same $\hsame$ and $\Cont$ rows.

No other coordinate is available in the carrier or in the orbit surface. Therefore every accepted read factors through the displayed scoped stack and cannot import host fixed-point equality, quotient map equality, or completed endpoints.
\end{proof}

\begin{theorem}[ContractionMapping completion readiness scope]
\label{thm:contraction-mapping-completion-readiness-scope}
The completion-facing readiness route for a $\ContractionMappingUp$ packet still requires a separate $\CompleteMetricUp$ row. The contraction packet exports only finite Picard tail-modulus data through $\PicardContractionUp$ and $\RegSeqRatUp$ rows, together with the structural $\mathsf{BHist}$, $\hsame$, $\Cont$, $\mathsf{Pkg}$, and $\NameCert$ evidence of the scoped source stack.
\end{theorem}
\begin{proof}
Start with the fixed-point readiness theorem. It already requires both the complete-metric handoff and the finite tail-modulus route before a $\BanachFixedPointUp$ consumer may proceed.

Use the scoped dependency surface. The visible source stack includes $\CompleteMetricUp$ only as a separate consumer row and includes $\RegSeqRatUp$ only for the finite threshold and tail-modulus surface.

Thus the contraction packet contributes readiness data, not a completion theorem. Since no row names a limit point, selected fixed point, quotient map equality, or ambient completeness proof, the route remains a completion-facing boundary rather than a fixed-point construction.
\end{proof}

\closureat{ContractionMappingUp}{seedStr}

\begin{closurestatus}{\ContractionMappingUp}
  \constructivestory{A $\ContractionMappingUp$ packet is generated from a $\MetricUp$ carrier row, a metric-distance row, a self-map row, a graph row, a rational contraction-bound ledger below one, an induced modulus row, a one-step $\PicardContractionUp$ route, componentwise $\hsame$ transports, displayed $\Cont$ routes, $\Pkg$ provenance, and a local $\NameCert$ row.}
  \theoryclosure{\obligationClosure}
  \scopeclosed{\autoref{def:contraction-mapping-carrier}, \autoref{thm:contraction-mapping-namecert-obligations}, \autoref{thm:contraction-mapping-picard-step-contraction}, \autoref{def:contraction-mapping-cauchy-orbit-ledger}, \autoref{thm:contraction-mapping-cauchy-orbit-contractivity}, \autoref{thm:contraction-mapping-banach-handoff}, \autoref{thm:contraction-mapping-complete-metric-handoff}, \autoref{thm:contraction-mapping-tail-modulus-readiness}, \autoref{def:contraction-mapping-regular-cauchy-modulus-surface}, \autoref{thm:contraction-mapping-tail-bound-extraction}, \autoref{thm:contraction-mapping-regular-cauchy-modulus-export}, \autoref{thm:contraction-mapping-complete-metric-regular-cauchy-handoff}, \autoref{thm:contraction-mapping-fixed-point-readiness}, \autoref{thm:contraction-mapping-orbit-uniqueness-window}, \autoref{thm:contraction-mapping-fixed-point-tail-seal}, \autoref{thm:contraction-mapping-complete-metric-consumer-package}, \autoref{def:contraction-mapping-scoped-source-stack}, \autoref{thm:contraction-mapping-scoped-dependency-surface}, and \autoref{thm:contraction-mapping-completion-readiness-scope} bind the carrier, Picard-step contraction, finite orbit ledger, Banach handoff, complete-metric handoff, finite tail-modulus readiness, regular-Cauchy modulus surface, fixed-point readiness, orbit-window uniqueness, endpoint-facing tail seal, complete-metric consumer package, scoped source stack, scoped dependency surface, and completion readiness scope for the constructive self-map contraction packet.}
  \formalstatus{\unformalizedV}
  \bridgestatus{none}
  \origin{human}
  \notclaimed{This chapter does not claim host fixed-point selection, ambient completeness, quotient map equality, bridge checking, host function extensionality, or a completed endpoint seal.}
  \upgradepath{Obligation closure requires checked carrier admission, classifier transport, graph exactness, rational bound stability, Picard-step compatibility, complete-metric handoff visibility, finite tail-modulus routing, and fixed-point readiness for the same finite packet.}
\end{closurestatus}
